





Brian was quicker than a guy his height should've been.  He stepped back out of the way of my jab, then turned his body in what I was learning was going to be a kick.  Thing was,  I didn't know where that kick would be directed, and he generally didn't hold back with his kicks the way he did with his jabs.  Knowing this, keeping to his instructions on being unpredictable, I threw myself forward and awkwardly tackled him.



His thigh caught me in the side as he brought his leg around, which hurt, but not as badly as the kick would have.  Even so, I succeeded in knocking him to the ground.  Any sense of victory I might have felt was short lived, because I fell with him, and he was more prepared for what came next than I was.  We hit the ground, he used the leverage of his hands and his still-raised thigh to heave me to his right.  Before I had my bearings, he flipped himself over in my direction and straddled me.



I jabbed a hand for his side, but he caught my wrist and twisted my arm around until my elbow was pointing at my bellybutton.  I grabbed at his shirt with my other hand, hoping to maybe buck him off me (fat chance), and he grabbed that wrist too.  He adjusted his grip on my twisted right arm and pinned my arms down against the ground, stretched out over my head.



``It's a start,'' he smiled down at me.



Realizing the position he had me in, feeling the pressure of his thighs against my hips, his weight resting partially on my lower body, I must've blown a synapse.  My thought process ground to a halt.  It didn't help that the first place my mind went was interpreting his `start' as being this position leading to something else.



``We keep this up, and you could be quite the scrapper,'' he elaborated.  ``When we were on the ground, here, and I pushed you to one side, you should have rolled with it.  Get yourself some distance.  If you were really quick about it, you could have even been on your feet before I was, which would be a good position for attack.''



\emph{``}Mmm,'' was the most coherent response I could manage.



``You going to let her up, or are you enjoying this too much?'' Lisa asked him, from where she sat on the couch.  She had her arms folded over the back of it, her chin on the cushion.  Her hands were folded in front of her mouth, hiding what I suspected was an amused smile.



Brian smiled as he stood, ``Sorry, Taylor.  You want to go a round, Lise?''



``Not dressed for it, it's too early in the day, and I wouldn't deny Taylor her fun,'' she spoke, without raising her head.  When I gave her an irritated look, she winked at me.



Brian and I stood and faced each other, then both of us hesitated, me staying just out of his reach.



``I'm surprised you're up for this, you two,'' Lisa commented, ``Aren't your legs sore from the jumping around last night?  You especially, Taylor.  You went on a run this morning, and now you're sparring?''



``If my knees could talk, they'd be screaming in agony,'' I answered her.  I raised my hand as Brian moved to attack while I was distracted, and he backed off again.  ``But staying active keeps my mind off stuff.''



``Everything okay?'' Brian asked me.  I shrugged, glanced at Lisa.



``Taylor went home,'' Lisa explained, ``Got in an argument with her dad, came back here.  Might be staying a while, yeah?''



``Yeah,'' I echoed her.



``Sorry,'' Brian sympathized.



``Me too,'' I spoke.  I stepped in closer, trying to provoke him to move, but he didn't fall for it.  ``I love my dad.  I never really had that phase others did, where I felt embarassed to be around him, where we didn't understand each other.  I thought we were closer than that, until last night.''



``Are things going to be okay?''



``Don't really know,'' I replied.  Changing the subject, I admitted, ``Okay, I'm stuck.  I'm standing here, facing you, and I don't know what I can do that isn't going to wind up with me getting hit or thrown to the ground.  I move forward, there's a million things you could do to kick my ass.  What would you do, in my shoes?''



``Honestly?  Hmm,'' he relaxed a bit, ``Good question.  I guess I'd go for the nearest thing I could use as a weapon.''



``Besides that.  There's nothing I could grab that would work for sparring without really hurting you.''



``I guess I'd do what you're doing, wait for the other guy to make a move.''



``Okay.  So move.''



He did. He stepped closer, feinted high with a kick, then ducked low to try and kick my feet out from under me.  I could handle that much – I hopped a little to avoid his foot as it moved beneath me.  Still, he was one step ahead of me, getting his footing with the extended leg and shoulder-checking me onto my ass.  I took his advice from earlier, going with it, scrambling backward to create some distance, but he had the advantage of having both feet on the ground.  He half-turned and followed after me, bringing his knee forward, stopping a few inches shy of my face.



``You're learning,'' he said.



``Very slowly.''



``You're learning,'' he stressed, ``You listen to what I say, you keep it in mind, and I almost never have to remind you of something twice.''



He offered me his hand, and as I reached up to take it, he gripped my upper arm.  I gripped his, and he hauled me back up to my feet.



``I come bearing coffee and breakfast,'' Alec pronounced, ``That a certain team leader was too lazy to fetch.''



``Aw fuck off, Alec,'' Brian replied, without any venom in his voice.  He let go of my arm to grab a coffee.  ``I grab you something nine days out of ten, on my way here.''



``That's your tax for the inconvenience of you living off site,'' Alec replied, moving toward the couch and handing Lisa and me our coffees.  Lisa took the paper bag and fished out some muffins, handing me one.  I sat on the couch next to her.



``So,'' Brian addressed us, as we all walked to the couches.  ``I think it's important to get a few things out of the way, now that we know who we're employed by, why, and our possibilities for the future.''



Bitch settled on the other couch with her dogs hopping up around her as she pulled her feet up beside her.  That left Brian to sit in the empty space between Alec and me.  I felt painfully conscious of where his calf and arm were touching my leg and shoulder.  I'd been running and sparring, I was probably sweaty.  Did I smell?  Would that gross him out?  I couldn't help but feel self conscious, but I would've stood out more if I did something about it.  I tried to focus on the discussion instead.



``First off, I don't think we should do a majority vote for this thing Coil proposed.  As far as I'm concerned, this is too important, too game-changing, for us to go ahead with it if anyone's going to be unhappy or upset.  We come to a consensus or we don't do it.''



I wasn't the only one to nod in silent agreement.



``Second, Alec, I gotta ask about what Coil said.  Past identity, your dad.  Is this something that's going to come back and bite us in the ass?''



Alec sighed and leaned back against the arm of the couch with a roll of his eyes, ``No chance we can ignore that?''



``I dunno, can we?''



``My dad runs his own group in Montreal.  I was working for him before anything else.''



``Who is he?'' Brian pressed.



``Nikos Vasil.  Heartbreaker.''



My eyebrows went up at that.



Lisa whistled, ``After Coil let that detail slip, I made a mental list of possibilities.  Had it narrowed down to four.  Heartbreaker was one, the pieces fit, but it was so hard to believe.''



``He's big,'' Brian said.



``No,'' Alec shook his head, ``He's scary.  He's newsworthy.  But he's not all that.''



Heartbreaker was what you got when someone had a power like Gallant, the ability to manipulate emotions, and absolutely no compunctions about using it selfishly.  Unlike Gallant, Heartbreaker didn't need to shoot you with any blasts of energy to affect you.  He just needed to be near you, and the effects were long term or permanent.



Despite Alec's attempts at downplaying who and what his dad was, it was hard to ignore the fact that I'd grown up hearing what this guy had done on the evening news, that I'd come across mentions of it online since I started browsing the web for cape stuff as a kid.  Heartbreaker found beautiful women, made them love him, \emph{really} love him, and formed a cult-like group with them serving him hand and foot, committing crimes for his favor.  They worshiped him to the extent they were willing to \emph{die} for him.  Drawn to their natural conclusion, his methods meant he had \emph{lots} of kids.  Alec included.



``Damn,'' I muttered.  I asked Alec, ``You grew up with that guy?''



He shrugged, ``It was normal to me.''



``I mean, what was it like? I can't even wrap my head around it.  Were the women nice to you?  What- how does that even function?''



``My dad's victims had eyes only for him,'' Alec said, ``So no, they weren't nice to me or my brothers and sisters.''



``\emph{Details,'' }Lisa said, ``C'mon.  Talk.''



``I'm not a talkative person.''



``Talk or I kick your ass,'' she threatened.



``Seconded,'' I added.



He scowled briefly, then crossed one foot over the other on the coffee table, settling deeper into the couch with his coffee resting on his belt buckle.  ``We had everything we could ask for, as far as money and stuff went.  Dad's victims took care of the chores, so the only thing us kids would have to do was take care of the babies sometimes.  Didn't have to go to school, but some of my brothers and sisters did just to stay out of my dad's way.''



``Why?'' I asked, ``Or is that a dumb question?''



``Eh.  It's hard to explain.  He cultivated us, bred for us, went miles out of his way to get us back if a member of his `family' was taken from him.  Mounted a freaking crusade if it came down to it.  But when we were around, he paid almost no attention to us kids.  When he did pay attention, it was to discipline us or test us.  Discipline usually meant getting a dose of paralyzing terror for not listening to him, insulting him or even looking him in the eye, sometimes.  Testing happened on our birthdays or if he'd had a bad day\ldots he'd try to set up a trigger event.  Not supposed to be so hard, given that we were second generation capes, obviously, but he started when we were eight or so.''



``How old were you?  When your powers showed?'' I asked, quiet, feeling intense pity not only for Heartbreaker's victims, but for the kids in that situation.



Whatever my feelings, Alec managed to look bored with the topic.  ``Hard to tell.  Since I didn't go to school, and nobody really kept records, I lost track of the years.  Ten or eleven, maybe.  I was his fourth kid to show powers, and there were eighteen or so of us when I left.  Most of 'em were babies, though.''



Which made him, not Grue, the one of us with the most experience and seniority.



Alec shrugged, ``So yeah.  I worked for him for three or four years.  We did jobs, I learned the family trade.  Called myself Hijack at first.  He started to get on my case.  I think maybe he was having trouble affecting me the same way he did before my powers kicked in, so he compensated for that by riding me.  Pushed my limits, made me do stuff that was dangerous, stuff that was hard on my conscience.  Wanted me to break, beg him to stop, so he'd have leverage to get me to do what he wanted.''



``And?''



``And he ordered me to kill this foot soldier for a group trying to push us out of their territory.  After I was done, he told me I did it wrong, that I had to do it again with a captive we'd taken, and I knew no matter what I did, he'd make me keep doing it.  Just another way of pushing my limits.  I had convinced myself I didn't care about the people I was hurting or about this guy I'd just killed, and maybe I didn't.  Maybe I don't, still.  Dunno.  But it was so pointless.''



He shrugged, ``I didn't see a real reason to stay.  Walked away.  Changed my name, got fresh ID, changed my villain name too.''



He'd killed someone on his father's orders, which made him the second killer in the group. Armsmaster must have dug up that detail & drawn the right conclusions after connecting Alec to his prior alter ego.



``When did this happen, this killing?'' I asked, quiet, ``How old were you when you killed that guy?''



``Hmm.  I'd been gone for about two years before the boss got in touch with me, which was about this time last year, so three years ago.  I would've been twelve or thirteen.''



Was that forgivable?  He'd been made to do it, he'd been in fucked up circumstances with no real moral compass to go by, still a kid.  The way he described it, though, it didn't sit well with me.  Cold blooded murder.



``You said he goes after his kids if they leave,'' Brian spoke, ``Will that happen here?  If he realizes you're one of his?''



``Dunno.  Maybe.  I'd bet he'd send one of my brothers or sisters to talk to me, ask me to come back before he did anything else.  If that happened, I'd probably leave before he came in person.''



``Or we could back you up,'' Brian pointed out.



``Or that,'' Alec agreed, apparently oblivious to the show of camaraderie.  ``Anything else?  Any more questions for yours truly?''



``Dozens more,'' I said, ``But I think we need to get to the other big topic of the day.''



``Yeah,'' Brian agreed.  ``I'm less than thrilled you didn't mention this, I have my concerns about the possibility that a guy like him might come after you, after \emph{us}, but there's nothing we can do about it for the time being.  Let's focus on more pressing matters.''



Lisa pulled her feet up beside her on the couch, ``Thoughts on the deal?  Before we vote?''



``Makes sense to me,'' Alec replied.  ``It's something I figured I'd end up doing eventually, controlling a territory, being boss of an area, letting the green roll in without any major effort.''



``Could be a lot of effort,'' I spoke, ``Depending on how secret he manages to keep this, and how successful he is.  If this goes bad, it means us against however many capes the Protectorate decides to throw at us.  We could wind up with the teams from Boston and New York coming to deal with the problem, if word gets out about what we're doing.''



``Call me an optimist,'' Alec said. ``I don't think it'll be that bad.''



``Taylor just reminded me of what I said about the bank robbery, and what wound up happening.''  This from Brian.  ``We've been successful because we, by and large, pick our battles, go on the offensive, and catch our enemies off guard.  In situations where we \emph{haven't} done that, and I'm thinking specifically about our fight with Bakuda, we really struggled.  That's when we came closest to getting killed.  Consider that we'll be the ones on the defensive, if we're holding this territory and taking on all comers.''



``We can work around that,'' Lisa replied, ``Plans, information gathering, pre-emptive attacks. I've got the inside info, and there's nothing stopping Taylor from using her bugs to keep an eye on the neighborhood.  Besides, Coil didn't say we couldn't hire other parahumans, just that anyone who wanted to work in Brockton Bay had to bend the knee to him.  So we could theoretically recruit other parahumans, if we needed to, bulk our forces.''



``My problem,'' I chose my words carefully, ``Is it sounds too good to be true.  What if it doesn't work out?  What if we wind up miserable, or if he screws us, or if he isn't as good as he thinks he'll be?  Do we walk away?  Will we be able to?''



``I got away from my dad,'' Alec said.  ``Would it be so hard to get away from Coil?''



I didn't have a good answer to that.  ``I guess we don't know enough about him or the resources he's got at his disposal to say.''



``I do have my reservations,'' Brian spoke, ``But I get the impression Coil's going ahead with this regardless of whether we're in or not.  I'd rather be in on this than sitting on the sidelines, watching it happen.''



``Yeah,'' I agreed, ``I think that right now, what we stand to gain by saying `yes', and being right, far outweighs what we stand to lose.''



``So, who's for the deal, then?'' Lisa asked us.



I raised my hand.  Alec, Brian and Lisa joined me in raising theirs.  That left the one person who hadn't participated in the conversation over Coil's deal as the sole nay vote.  Bitch seemed unconcerned as she rubbed Brutus' shoulder.



``What's up?'' Brian asked her.



``I don't like it.  Don't trust him,'' she didn't raise her eyes from Brutus.



I leaned forward, ``Not saying you're wrong in not trusting him, but why?''



Angelica, the one eyed, one eared terrier, nuzzled her, and Bitch scratched her behind the ear.  Bitch explained, ``He talks too much.  Only reason people talk like he does is if they're covering something up.''



``I don't think he's covering anything up,'' Lisa said, ``My power would probably clue me in if he was hiding something.''



``I'm going with my gut, and my gut says no.  Besides, things are fine the way they are.''



``But they could be better,'' Alec said.



``Your opinion, not mine.  We done here?  You said we wouldn't accept the deal unless everyone was cool with it, and I'm not.''



Brian frowned, ``Wait.  I assumed we'd discuss this, hear each other out.''



``Nothing to discuss,'' Bitch stood up and whistled twice.  Her dogs hopped down from the couch to follow her.  ``I'm going to work.''



``Come on,'' Brian said, ``Don't-''



Lisa stopped him, ``Let's wait, then.  He said we had a week, we can afford to wait a day or two.  Bitch, go do your thing, get it out of the way.  But maybe try to be more open to negotiation and discussion when it comes up again.''



Bitch's eyebrows knit together in a glare, not directed at anyone in particular.  She turned her attention to collecting the things she needed – plastic bags, a few energy bars, leashes, and a backpack with a bright blue plastic stick jutting out of a gap in the zipper.



``Hey,'' I spoke up, ``Can I come with?''



I'd told myself I wanted to connect with these guys, and that wasn't going to happen if I just sat back and participated only when invited.  I had to put myself out there.  Given what I was giving up to be here, I figured I owed it to myself.



Bitch, though, was less than impressed.  The look she gave me could have sent a small animal fleeing for its life.



``Fuck you,'' she spat the words.



``Hey.  What?'' I was stunned.



``You want to come and bug me to change my mind.  Well fuck you.  You're not coming into my space, getting in my business, to make me do or say anything I don't want to do.''



I started to raise my hands, in a placating gesture, but I stopped myself.  Bitch had a different standard for handling social situations.  She didn't understand stuff like tone, stress, sarcasm, and precedent had led her to assume sarcasm and aggression from any statement.  And it wasn't just statements, I had a suspicion that the \emph{gesture} of raising my hands could be seen as aggressive, or something like an animal trying to make itself look bigger, intimidating.



I had to communicate with her in a way that left the least room for misinterpretation.



``You're going to take care of the rescued dogs, right?  That's what you do when you go out?  Your `work'?''



``None of your business.''



``Coil said you're overloaded.  I'm offering an extra set of hands, so you can give the dogs more of the attention they need.''



``Bullshit.''



``Enough,'' Brian started to rise, ``You need to calm down-''



I put my hand on his shoulder and pushed him down.  ``I'm fine.  Rachel, I'm going to make you a deal.''



Her eyes narrowed.



``I thought my last deal was pretty fair, so hear me out?''



``Fine.''



``Let me come along.  I'll help out where I can, we'll maybe talk, but we \emph{won't} talk about Coil, unless you bring it up.  In exchange, if I \emph{do} bring it up, or if I try to manipulate you one way or the other, you get a free shot at me.''



``A free shot.''



``One punch, however you want it, wherever you want to stick it.  I know Brian said something about there being no repeats of the day we met, no fighting inside the group or whatever, but this would be a freebie.  Totally allowed.''  I glanced at Brian, who only gave me a concerned look and a small, tight shake of the head.



``Nah,'' Bitch answered, ``You'll just piss me off some other way.''



Impulsively, I told her, ``Then how about this?  If we finish, we get back here, and it turns out I've ruined your day, you get that free shot.''



She stared at me for a moment.  ``So I just got to put up with you for a few hours, and then I get to knock your teeth out?''



``\emph{No},'' Brian said, raising his voice.



``\emph{Yes},'' I told her, giving Brian a pointed look.  ``\emph{If }I mention the meeting before you do, or if I piss you off.''



She looked me over, ``Whatever.  If you're that eager to get hit, it's your funeral.''  She took off the backpack and threw it at me.  I caught it with both arms.  Heavier than it looked.



As I hurried her way to get my running shoes on, Alec hissed at me, ``You're \emph{crazy}.''



Maybe.  Probably.  But I couldn't think of a better way to reach out to Bitch.



I hoped this wasn't something I was going to regret.













