





Bitch led the way as we traced a winding path through the Docks.  Her dogs trotted at her side, occasionally stopping to sniff, but never rushing ahead or lagging so far behind that they pulled on the leash.



Glancing at her, I could see how she was more at ease, like this.   When she was walking with the dogs at her side, I could see that the lines of her face were softer, there was less tension in her body.  She wasn't quite so guarded.



I'd sort of assumed that her days of being homeless and fending for herself were the bad days, to her.  That it was a step up, being with us.  I was beginning to reconsider whether that was entirely true, seeing her stride down the streets and alleys with her dogs beside her.  Here, she didn't have to worry about dealing with people and the social maneuverings she could no longer grasp.  This was what she was used to.



She glanced my way, and a shadow of irritation touched her expression.



I was intruding on her domain, spoiling that.  If I slipped up and pissed her off, I'd be lucky to get hit just once.



I knew we were close to our destination when I heard the barking.  Angelica yapped back in reply, cranked herself up to `excited frenzy' mode and rushed forward, pulling on the leash.  Bitch stopped her, directed her to lie down with a motion of her finger, and we waited.  When Angelica relaxed and put her chin on the ground, we moved forward again.



We didn't get three steps before Angelica pulled again, provoking the repetition of orders and another minute long wait.



The third time it happened, Bitch gave me a dark look.  As though it were my fault, or more probable, she might have been anticipating impatience on my part.  I didn't really mind, though.  It wasn't like I had anywhere to be, and it was interesting to see her process.



``How long have you had her?''



``Five months.''



``That's pretty amazing,'' I conceded, ``I mean, she was abused before you got her, right?  So even with having to get her past that, and she's already better trained than any dog I've seen that isn't yours.''



``Walk on,'' she instructed Angelica.  When Angelica didn't pull, Bitch handed out treats to Brutus, then Judas, then Angelica in turn, without breaking stride.  ``Dogs learn from their pack.  She learns some from imitating Brutus and Judas.''



I nodded.



``Most dog owners are retards anyways.''



``I can believe that.''



We approached the building that all the barking was coming from.  The rusted skeleton of a small crane stood atop a partially constructed building.  Bitch opened the door and waited until I was inside before closing it and latching it shut.  I could hear scratching at the door just past the first room.



When the second door leading further into the building was opened, a tide of dogs nearly bowled us over. I couldn't count them, but there were more than ten, less than twenty.  All sorts of breeds, different sizes and shapes.



As Bitch moved forward as though the dogs weren't there, I struggled to even stand.  I leaned against the front door for balance, and all I could think about was that moment Bitch had set her dogs on me, back when we first met.



I couldn't afford to appear weak in front of Bitch, so I avoided asking for help.



Cement was laid out over nearly half of the building interior, as the floor or foundation, but the work had been interrupted and abandoned partway through.  There were areas where crushed stone had been laid out in preparation for the cement pour, and a combination of wind and rain had mixed regular dirt into the crushed stone a long time ago.  Any spot inside the building that wasn't covered in concrete was marked by patches of grass and a few scraggy weeds.



Three walls of the ground floor were erect, plywood and drywall bolted to wood frames, with cement blocks piled against most of the exterior walls.  Enough had been done at the front of the building for the construction workers to have started laying out a second floor, providing an overhang between the ground floor and the sky to keep things more or less dry.   Things were too much of a mess for me to tell if the far exterior wall had been left incomplete or if had fallen down.  It stood open to the environment, letting rays of dusty sunlight inside.



Bitch headed to a wood pallet stacked with bags of dog food, which rested atop a pallet of bricks.  She drew a knife across the top of two bags and let them empty into a trough sitting below.  I was grateful when most of the dogs around me rushed off to get their food.



The reprieve didn't last long.  Several of the dogs began fighting in front of the trough.  A black lab, snarling with his expression pulled into something grotesque, chased a smaller dog directly toward me.  The little dog collided with my legs, and with the lab hot on her heels, it started fighting tooth and nail in its own defense.  A bigger dog, longer and lankier than the lab, with very short fur, crossed the room to join the skirmish, protecting the little one.



``Bitch?''  I asked, doing my best to keep my voice calm as the dogs fought beneath me, bumping into my legs.  I backed up, but they brought the fight right to me once again.



``The black one is Sirius.  He's the newest, not used to things.  He'll get better as the other dogs socialize him and I get a chance to train him.''



``They're, uh, really going at it,'' I winced and pulled one leg off the ground to keep it out of the way.



``Let me know if he draws blood.''



The fighting was nerve wracking, conjuring up very vivid memories of Bitch's dogs terrorizing me.  Why did this spook me so much when being around her dogs in monster form didn't make me that nervous?



Shutting my eyes, I drew on my power.  My objective wasn't to do anything with it, but simply to get a little outside my own head, achieve a greater perspective.  Focusing on the big picture, seeing myself as a very small figure against the backdrop of a whole neighborhood, I was able to center myself.  I could ignore the hairy animals shoving up against my legs, jumping up at and around me, pressing their cold noses against my hands and arms.



A mass of bugs in my immediate vicinity lunged between my legs.  My eyes snapped open, and I saw the culprit, placed my hands on him, the dark furred lab.  It wasn't fleas, either, or ticks or anything like that.  It was a denser mass.  The closest parallel I could draw would be a wasp nest.  Or maggots in a trash bag.



``Bitch,'' I spoke, cautiously.



``What?'' She sounded\ldots annoyed was the wrong word.  She sounded ready to kill me, for interrupting her from setting the dogs up with fresh water.



``I think one of these guys is really sick.''



Her head snapped in my direction.  ``Show me.''



The dogs stopped fighting as she stalked toward us.  I took the opportunity to gingerly take hold of Sirius's collar as she ushered the rest away.  She glowered at me, ``Explain.''



It was hard to organize my thoughts, even without accounting for her intense scrutiny.  ``Worms.  But not, like, tapeworm.  I-I can't see through their eyes or anything.  Um.  I don't know what they are, so I can only tell you what I know.  They're mostly juvenile, only a few adult, um-''



``Above the heart, here?''  She pointed to a spot low in his chest.



I nodded.



``And the arteries?  There's one from here,'' she pointed at the lab's shoulder, ``To here?'' she traced her finger along his spine.



``That's where a lot of them are.  But they're not just there.  They're \emph{everywhere} inside him.''



``Fuckers.  Those fuckers,'' she growled.  ``I warned them.''



Taking hold of the lab's collar, she ordered the dog, ``Come along, Sirius.''



The dog resisted until Brutus moved forward, then went along, though he still pulled and twisted against the grip on his collar.



``I don't know dogs,'' I said, following her into the herd of dogs just inside the building.  ``I never had a pet, so I'm clueless here.''



``It's heartworm.  Something dogs are \emph{supposed} to take medicine to prevent, every month.''



``The owners didn't, then?''



``The \emph{shelter} didn't.  Lazy, cheap-ass mother\emph{fuckers}.  This is the \emph{second} dog I got from that place that wasn't taken care of.  And people who \emph{do} adopt get a sick dog?  Fuckers, fuckers, fuckers.''



``What are you going to do with him?''  I tried to ignore the dogs milling around me, to keep moving forward and follow Bitch.



``\emph{We} are going to help him.''



I shook my head.  ``I don't think I can get the worms out without hurting him.  I mean, they're in his bloodstream and the closest thing to an exit would be his lungs, and I think they would bleed too much.  I'm not even sure I can move them.''



``Grab that chain.''  She pointed across the room, still holding on to Sirius.



I saw several lengths of heavy chain, spotted with rust, looped up and hung on the wall above a pallet of weather worn brick.  I hurried over and hauled it down.  It was heavy enough I had to drag it on the grass to bring it to her.



``Backpack,'' she told me.  I took it off and handed it to her.  She opened the front and handed me a carabiner, a metal loop with a locking hinge.  ``Go tie the chain to something solid.''



I did, looping the chain around the base of the crane that was bolted to the concrete pad, toward the center of the room.  I fed the length through the carabiner  and headed back to Bitch.



Judas, Brutus and Angelica were already halfway to full size.   Bitch took the chain and began extending it around the struggling dog, winding it through a half dozen carabiners so it extended around his neck, body and stomach, and between his legs.



``What's going on?''



``I'm using my power on him.  And he's not trained.''



``Wait.  Didn't a dog kill some people, back when you first had your powers?''



``Yup.''



I felt my heartbeat speed up a notch.  ``So this is really dangerous.''



``Yup.''  She tugged on the chain at his neck.



``Okay.''  I exhaled slowly.  ``What can I do?''



``Keep out of the way for now.''



Sirius started to grow.  Muscles rippled underneath his black coat, and he yelped, pulling away.



``Couldn't we maybe get him tranquilized, first?'' I asked, watching the lab try to get away, despite the chains binding him.



Bitch held the length of chain in her hands, keeping him in place.  ``No.  My power would burn away the drugs.''



``He doesn't like it.''



``It takes getting used to. But this is better than what he'd go through if a vet took care of it.  Safer.''



\emph{Not for us}, I thought, as Sirius pulled back.  Bitch pulled him closer to her, shifting her grip to the chain at his neck and chest to feed the slack through it and give Sirius more room to grow.  His ears were pulled back, his face etched in fear and rage, teeth bared.  I would have been terrified he would snap at me, given how easily he could take half of someone's face off with a single bite, but Bitch never flinched or broke eye contact with him.



Something moved to my right, and I saw Brutus pacing.  The other dogs, the ones I didn't know, stayed back a fair distance, kept at bay by Brutus's watchful presence.



There was a sound of shuffling chain as Bitch adjusted the chain again.



``Judas, Angelica!'' she called out, releasing Sirius and backing away.  ``Hold!''



Sirius, pupils narrowed to dots, lunged at her.  Judas stepped between them, while Angelica struck at the lab from the side, knocking him to the ground.  In a moment, the two dogs were on top of him, Judas holding Sirius's throat in his jaws, while Angelica lay astride his hindquarters.  Even with two full size dogs piled on him, Sirius managed to put up a struggle.



``The heartworm?'' Bitch glanced at me.



I felt out with my power.  Whatever was going on inside Sirius' body, the worms were being churned up, disintegrating and dissolving.



``Almost gone.''



She nodded.



She turned her attention to Sirius, who was lying prone, his chest heaving.  ``Heartworms have a bacteria inside them.  When they die, the bacteria gets released into the dog.  Having a vet treat it is a long process that involves injecting arsenic into muscles and lots of antibiotics.  Like this, his body won't just kill them, but it can kill the disease.  He'll be fine by tomorrow.''



Sirius let out a long, mournful noise, somewhere between a whine and a howl, loud enough that I had to turn my face away and cover my ears.



When I was sure he wasn't about to do it again, I dropped my hands.  I asked Bitch, ``Have you done this before?''



She shook her head.  ``I've used my power on most of them, but only a little, to keep them healthy.  Sirius is the only one I've made this big since Angelica, Brutus, Judas and Rollo.''



I almost asked who Rollo was, but I kept my mouth shut.  It was a habit of mine, I found, that I usually pushed a conversation with Bitch too far, gave her an excuse to get pissed at me.  I could prioritize other things over my curiosity.



Besides, as I thought on it, I realized Rollo might've been the first dog she used her power on.  The one with the body count.



``Time?'' She asked.



I found my cell phone, fumbled with it to press a button and display the time.  ``Nine minutes past eleven.''



``We'll give it fifteen minutes,'' she reached for the chain and held it.  ``Takes about that long for it to wear off.''



``Okay.''



``I don't need you here.  If you want to be useful, there's a shovel by the door.  You can go pick up the shit in the short grass over there.''



``Fuck you,'' the words spilled out of my mouth before I could censor them.  I wasn't positive I \emph{wanted} to censor them, but it bugged me that I'd done it without thinking it through.



``What?'' she growled at me.



``Fuck you,'' I repeated myself, ``I came to help.  Thought maybe I was helping, by pointing out what was wrong with Sirius.  That doesn't mean I'm going to be your slave, or that it's an excuse to give me the worst jobs.  You want me to pick up the poop?  Cool, but I'll do it when you've got a shovel in your hand too, and you're working beside me.''



``You told me I could hit you, free and clear, if you pissed me off,'' she threatened me.



``Yeah, but if you do it here, for this reason, I'm hitting back,'' I didn't move my eyes away from hers, even as every awkward part of me twitched to look away and leave.  If she really did default to interpreting social interactions in dog terms, then eye contact was important.  I didn't know much about animals, about dogs, but I did know that it was the submissive dog, the dog lower on the totem pole, that backed down.



``I've got Brutus, you wouldn't win the fight,'' she told me.



\emph{Almost definitely true}, I thought.  But I couldn't give in.  I resisted the urge to look at Brutus and told her, my voice low, ``You want to go there?  Try it.''



She set her jaw, stared at me for several long moments.  Then Sirius made a noise, a smaller version of that whimpering howl he'd made earlier, and she turned her head.



I waited a minute, watching as Sirius got the strength to struggle again, nearly standing up, before the weight of the other two dogs pressed him down again.



``Bitch- Rachel.  I'm getting the impression you might be here a while, to keep an eye on Sirius, give him some attention after he's back to normal so he knows everything's okay?''



``What about it?''  Her voice was hard, and she didn't look my way.



``Do you want me to pick up something for lunch, so you can stay here with him?''



``\ldotsFine.''



``You know this area better than I do.  Where-'' I stopped.  I needed to convey more self confidence than simply asking her for the info.  She might even see it as begging.  I told her, ``Tell me where to go.''



I was crossing my fingers she wouldn't go nuts over me giving her an order.



She was too preoccupied with watching Sirius to argue with me.  ``There's a Greek food stand if you walk in the direction of the Boardwalk.  You'll smell it before you see it.''



``Okay.  What do you want?''



``Anything with meat.''



``I'll be back,'' I told her.



She didn't reply, leaving me to make my way through the crowd of dogs to the front door.  I stuck my shaking hands into my pockets and headed off to grab our lunch, leaving Bitch with the monster in chains.





