





I was nervous, returning to Bitch's spot with lunch in hand.  It wasn't just that I'd left her alone with an uncontrollable beast composed almost entirely of fangs, nails, bone and muscle.  It was that it was lunchtime.



Between countless run-ins with the bullies, getting in contact with the Undersiders and the bank robbery, it felt like stuff seemed to go down around noon.



I was relieved when I got back and there wasn't any carnage.  A dozen or so dogs greeted me, many poking their noses into the paper bag I held.  I navigated my way through them to Bitch, who was sitting on a pallet of concrete blocks by the open back wall.  Sirius was lying beside her with his head on her lap.



``Food?'' I offered.



She reached down, so I got a chicken souvlaki wrap and a coke out of the bag and handed them up to her.



As she peeled the paper away from one end of the wrap, I found myself a spot to sit on a part of the wall where it was incomplete or damaged.  The weather had worn at the concrete blocks, and some greenery had managed to grow in the cracks, making for a not entirely uncomfortable seat.  Outside, behind the building, there was a field of uncut grass surrounded by chain link fence.  As they lost interest in the food, dogs wandered out there, chasing one another or baiting others into playing, trampling that long grass flat enough that we could see them.  The view of their playing was accompanied by a soundtrack of endless barks and snarls.



A white dog with a nub of a tail and chestnut colored patches on its body and over its ears approached me, sitting to stare at me as I took my first bite of my wrap.



I swallowed, and I told the dog,  ``No.  This is too good to share, and it probably wouldn't be good for you anyways.''



The dog cocked its head quizzically.



``You are awfully pretty, though,'' I told it.



I heard a scoffing noise from Bitch's direction.  I turned her way just in time to see her glance away.



``What?''



``You should never own a dog.''



That was fairly harsh, especially coming from her.  ``What are you basing this on?''



``Most dog owners are retards, and the \emph{most} retarded are the ones who pick a dog because it's cute, or because its \emph{pretty}, without knowing anything about the breed, the temperament, the dog's needs.''



I sighed, ``Fuck off, Rachel.  I can say it's a pretty dog without saying I'm going to take it home.''



``Whatever,'' she didn't take her eyes off the dogs in the back field.



``No, don't brush me off.  You want to start something, fine.  But if you do, you gotta hear what I have to say.  \emph{Listen} to what I have to say.  Acknowledge me, damn it.''



She turned to glance at me.  She wasn't frowning or glaring, but her gaze was so dispassionate it made me uncomfortable.



``Come on, you know me pretty well.  All the others describe me as careful and cautious, though I'm not entirely sure why.  Do you really think I'd pick something as important as a dog, a new addition to my family, without researching, first?''



She didn't reply.  Instead, she turned her attention back to the dogs outside.



``Right,'' I said.  ``I wouldn't.''



I didn't press things any further.  We finished our wraps, I dug one piece of the foil-wrapped baklava out of the bag, set it down on the paper from my wrap and bunched up the foil around the remainder to throw up to Bitch.  When I was done eating my dessert and licking my fingers clean, I hopped down from my seat on the wall, found a ball and started throwing it for the dogs.



``Here,'' Bitch told me.  I turned around, and she handed me the blue stick that had been jutting out of the zipper of the backpack.  It was plastic, molded to have a handle with finger-holds on one end and a cup on the other.  As a dog brought the ball to me, I experimentally pressed the cupped end down on it, and the ball snapped into place.



When I whipped it forward, the ball went flying, five times as far than it had when I'd used my hand.  Most of the dogs stampeded after it, racing to be the first to grab it or chasing after the ones in the lead.



It was nice, enjoying the sunshine, playing with the dogs, having no responsibilities or pressures for the moment.



I turned to look over my shoulder.  ``Can you tell me about some of them?  The dogs?''



Bitch frowned, but she didn't refuse me.  ``This is Sirius.  He was bought as a puppy for some twelve year old, then grew too big and unruly to stay in the house.  He was caged outside and ignored, his nails grew too long, and he wound up with an infection in his foot.  They decided it was easier to leave him at a shelter than pay for medical care.  Since he wasn't trained or socialized, he came off too wild and excitable to get adopted.  I got him in the week he was due to get put down.''



``That's fucked up,'' I looked at Sirius, who was sleeping.  ``How do you know the story?''



``I know some people that volunteer at shelters, from when I used to.  They let me know if there's a dog that deserves a second chance.  Not that many \emph{don't}.''



``Ah.''



``The one you were talking to a few minutes ago is Bullet.  She's the smartest in the group.  Her breed craves exercise, they're meant to run around all day with hunters\ldots except she was used as a beta to warm dogs up for one of the dogfighting rings around here and her shoulder was torn up pretty badly.  Even with the shoulder healed as well as it's gonna get, it hurts too much for her to run as much as she needs.''



I spotted Bullet in the crowd.  Sure enough, she was lagging behind the rest.  I thought maybe she was favoring one leg.



``If your power heals, why doesn't it help her?  Or Angelica's eye and ear?''



Bitch shrugged.  ``Lisa said it has something to do with me making a `blueprint'.  It's babble to me.  All I know is that it doesn't help older health problems.  It gets rid of disease and cancer, and parasites, and most damage they take when they're big.  That's all.''



``I think I get it,'' I told her.  I looked at Bullet, who had stopped running and was sitting in the middle of the field, watching others run.  ``Do they all have stories like that?''



``Most.''



``Damn,'' I felt a pang of sympathy for the animals.



The herd of dogs returned to me, and a shaggy dog dropped the ball at my feet.



``Good dog,'' I told it.  I threw the ball, aiming to get it near Bullet, and the herd of dogs rushed off again, with more than a few excited barks.



Bitch and I weren't conversing, but neither of us were conversation people.  I was too socially clumsy to maintain small talk for any length of time, and Bitch was\ldots well, she was Bitch.  So we sat, minutes passed between each exchange of dialogue, and it somehow didn't bother me.  It was letting me pick and choose what I was talking about very carefully.



``It's too bad dogs can't have trigger events,'' Bitch mused aloud.  ``If they did, some people might think twice.''



I could have argued the details, pointed out that most people weren't aware of the ins and outs of trigger events, I could have argued that some things could get \emph{worse} if dogs could get powers.  It didn't feel necessary.



``Yeah,'' I agreed.



That was the extent of that dialogue.  We enjoyed another long silence and the dogs competed with one another to fetch the ball.



The sound of a breaking bottle and very human shouts disturbed our peace.



``These guys again,'' Bitch snarled, moving Sirius' head from her lap and hopping down from her seat on the pile of concrete blocks.  The black lab turned his head to watch as she stalked towards the front of the building.  Bitch whistled for her dogs and Brutus, Judas and Angelica rushed to her side.



``What's going on?'' I called after her, moving to follow.



``Stay inside,'' she told me.



I did as she asked, but that didn't mean I didn't try to get closer, to get a better picture of what was going on.  I approached one of the boarded up windows at the front of the building and peeked through a gap in the plywood.



Bitch had her dogs standing around her, and she stood opposite a group of seven or so people.  They ranged from thirtyish to twelve in age.  It wasn't hard to figure out who they identified with.  Half of the guys were blond or dyed blond, and the others had shaved heads.   The youngest was a twelve-ish girl who'd taken a razor to her scalp, too, leaving only her bangs and the hair hanging around her ears and the back of her neck.  The detail that confirmed my suspicions of their affiliation was the number eighty-three that I saw etched on one of the guys' t-shirts in permanent marker.



The white supremacists loved codes in numbers.  If you were suspicious about whether a number was one of their codes, the number eight was a good clue, since it cropped up a lot.  The eight referred to the 8th letter of the alphabet, H; Eighty-eight stood for H.H. or `Heil Hitler', while eighteen pointed to Adolf Hitler in the same way.  The eighty-three wasn't one I'd seen before, but I knew it would have stood for H.C\ldots Heil something.  Heil Christ?



In any case, these numbers had been a way to keep one's racist feelings on the down low, around those that weren't already affiliated, until Kaiser's predecessor formed Empire Eighty-Eight here in Brockton Bay.  The move had pushed an ultimatum on the more secretive racists in the area, forcing them to either join the aggressive, active group in the public eye or retreat further into hiding.   It had also drawn crowds of the more diehard white supremacists from the surrounding regions to Brockton Bay.  When people with powers, Kaiser included, started to congregate in the group, Brockton Bay became something of a magnet for those sorts.  One of the bigger collections of racists above the bible belt.  Quite possibly the biggest congregation of racist supervillains.



The day Empire Eighty-Eight had gotten its name hadn't been a good day for our city.



A guy, thirty or so, was holding a carton of empty beer bottles.  He held one by the neck, tossed it into the air and caught it again, then whipped it in Bitch's direction.  I flinched more than she did as it shattered explosively against the front of the door.



``We told you to get of here,'' he sneered at her.



``I was here first.''



``Doesn't matter.  We're claiming this neighborhood, and that barking is driving me up the fucking wall.''



``You've said so before.  Try earplugs.''



He grabbed another bottle and threw it, hard.  Bitch had to lean out of the way this time, to keep it from hitting her shoulder.



``Can't do business wearing earplugs, you dumb whore,'' the man put his hand on the head of the partially bald girl, who made a face at Bitch.



``Then don't do business.  I don't care.''



He reached for another bottle, then stopped.  A slow smile crossed his face as he looked to a teenage boy that was standing just beside the bald girl,  ``Thing about something as goddamn irritating as that barking, is it gets us talking about how we could deal with it.  Tom, here, had my favorite suggestion.  He said we could soak hot dogs in antifreeze and throw 'em into the field back there.  Whaddya say?''



\emph{Fuck}. I looked around the inside of the building for something I could use as a mask, but there wasn't anything.  Why hadn't I brought my costume?  The situation was a hair away from devolving into a bloodbath, and my civilian identity was plain to see.  I couldn't even work from inside the building, without risking that someone might have heard about my power or how I operated, and come in after me.



I could only see Bitch from behind, but I saw her turn her head to evaluate the group.  Maybe sizing up how long it would take her dogs to murder them all.



``If you were going to do that,'' she said, ``You would have done it before now\emph{, and }I'd kill you for it.  Either you're too scared to really do something about it, \emph{which you should be}, or Kaiser told you hands off.''



It was the last attitude I would've expected from her.  Bitch, being level-headed?



The man with the bottles sneered, ``Nah.  See, we heard that howling earlier.  So did some of our neighbors.  Kaiser did tell us to play nice, but way I figure it, if we tell Kaiser you started this shit, and he asks around to check our story, he's gonna hear there was howling before there was fighting.''



``You know who I am,'' Bitch threatened them, ``You know my abilities.  You're really going to fuck with me, here?  With my dogs around?  \emph{Really}?''



I heard, rather than saw, the sound of a gun cocking.  The teenage boy, who I identified as Tom, raised a gun in Bitch's direction.



``Still think you're tough?'' the man mocked Bitch, ``Guns are the great equalizer, y'know?  My son here wants a place in the Empire, and to do that, he's gotta earn his stripes.  Killing you would be a good way to go about it, I'm thinking.''



I didn't wait to hear the rest of the dialogue.  There was no way this wasn't going to come to violence, now.  I pulled off my shoes, then ran in my sock feet across the concrete floor, keeping as low as I could.  I found the knife that Bitch had used to open the bags of dog food, then stuck it in my back pocket.  Still nothing I could see that would work as a mask.  I wasn't even wearing a sweatshirt or enough extra layers to use a piece of my clothing for a mask.  It had been too warm a day.



Which left me one very unpleasant option.



I exerted my power, and was glad to find that the grassy field and the half built building had a fair supply of bugs to work with.  Grasshoppers migrated my way, and I emptied a wasp nest that nestled in the wall above the unfinished second floor.  Blackflies that had been enjoying the copious amounts of dog waste flew my way, and innumerable ants and spiders formed the remainder of the swarm.



All together, they streamed my way to gather on my skin, crawling up my legs and torso, some turning downward to cover my arms.  As one, they covered every inch of my body, even creating a mass over my mouth and glasses to obscure everything.  It didn't tickle as much as I thought it might, but I did shudder.



I'd need a shower after this.  Ten showers.  And I'd pay to use a gym or pool or something, so I didn't have to endure the craptacular shower at the loft while I scrubbed my skin raw.  Ninety percent of my rationale for designing a costume that covered my entire body was for this exact reason, damn it.



\emph{Why} hadn't I brought my costume?  Why?



I flinched at the deafening roar of a gunshot.  Waited with my breath held, until I heard the murmur of conversation at the door again, Bitch's voice.  A warning shot?



I grabbed my cell phone from my pocket and sent a text out, selecting Brian, Lisa and Alec as the recipients:



\msgbox{Half a dozen skinheads here.  At least one gun.  Need backup.}



My phone vibrated with a reply a few seconds later. Brian:



\msgbox{Omw.  was headin home.  will take minute.}



No immediate reply from the other two.  My phone displayed the time as 1:38.  Close enough to lunch for me to mark it as a continuation of the trend.  I was going to develop an anxiety disorder over this.  I texted him directions, informing him to look for the building with the crane.



Enough bugs had gathered to cover me, with plenty to spare.  I'd wanted to be absolutely sure I was covered, so I piled them on top of one another, several layers deep.  It was stifling.  I was forced to breathe through my nose, and my vision was obscured by the bugs that had collected on my glasses.   More than that, it was \emph{hot} in the midst of the dense swarm.  Still, I was happier enduring it than risking being identified.



I looked out the nearest boarded up window that I could see through, and saw that the group hadn't moved.  The man with the bottles said something, but I couldn't make it out.  My leaving to grab the knife and send the texts had carried me out of earshot.



I ran back to the front door, keeping to the same half-crouch as before, to ensure nobody saw me through the gaps in the boards on the windows.  I pulled my shoes back on, straightened, took a deep breath, and opened the door.



``Jesus fuck!'' a twenty-something skinhead cursed as I moved to Bitch's side.  I had a vague sense of what I must have looked like – a tower of swarming insects with vague human definition to it, giving the loose shape of a head, with vague indents in the `face' where my eyes were.



Even Bitch's eyes widened a fraction as she saw me.



``The hell?'' she muttered.



I stayed quiet, keeping my attention on their group.



Bottle man looked me over, then spoke in a low voice, ``Tom, was it?  Would you do the honors and deal with this amateur horror show?''



The teenage boy, turned the handgun my way, pointed at chest level.  He smirked and grinned, ``My pleasure.''



The scene with Bakuda and her minions hadn't been so different.  Only difference was, Tom didn't hesitate a second when it came to pulling the trigger.



The sheer force of the gunshot left me reeling, and it hadn't even hit me.



I had dropped to a crouch as I stepped outside, leaving most of the bugs where they were above me.  Some had fallen down, but the overall structure had remained more or less stable, each of the bugs gripping one another and spreading out enough to fill in the gap of the vacated head and chest area.



From what my bugs had experienced, I knew the shot had passed only inches above my head, around the center of my chest.  The swarm down where I crouched was denser, to support the structure above them, so I couldn't see through them as easily.  I could only wait with my breath held, hope that the bugs offered me enough cover to hide my real self.



``The fuck?'' Tom spoke.  I moved the bugs in front of my eyes so I could get a partial look at him, and saw him backing away, gun still raised.



I'd borrowed a trick from Grue, and figured it only made sense to borrow one from Tattletale, too.



When I spoke, I hissed the words, and at the same time, I had every bug in the swarm make noise: buzzing, chirping and droning in time with my words, doing everything I could to sound less human.  ``Guns are not going to work when my body is like this.''



Putting my hands on the ground, bringing the upright mass of bugs with me, I crawled forward a step.  I saw almost everyone in their group move away.  Only the man with the bottles remained where he was, and he used one outstretched arm to keep Tom from retreating as well.



My ploy was working.  As Tattletale had done with Glory Girl and Panacea, then again with Bakuda, I could sell the idea I had powers I didn't to mislead and misdirect.



``Shoot, boy!''  The man tightened his grip Tom's shoulder.



The teenager obeyed, firing thrice more into the swarm, aiming too high to hit me.  Two more shots struck where my chest would have been.  The third passed through my fake `head'.



Tom, his eyes wide in alarm, decided to change targets.  He swung his arm to my right to point his handgun at Bitch.



I lunged forward, drawing the knife and swinging it in one motion.  I stabbed Tom in the thigh, as Bitch simultaneously evaded to one side.  Through a combination of my attack, Tom having to adjust his aim and Bitch's movements, the shot went astray.



As Tom fell over, I collapsed the swarm on top of him.  Avoiding touching him directly, I pulled the gun from his hand, retrieved my knife, and stabbed the point of the knife down on his palm to eliminate any possibility of him retaliating or grabbing for his weapon.



On an impulse, I drew the knife across his forehead.  According to Brian, cuts to the forehead were rarely serious, but they bled enough to \emph{look} like they were.  It was a fact that people that staged fights often played up, and a technique boxers used to blind their opponents with blood in the eyes.



I left some of my bugs on and around Tom as I moved away from him.  He screamed frantically and struggled to crawl away.



It was more brutal an approach than I might have liked, but as I interpreted it, any effect I generated by injuring him like this, would hopefully prevent others from joining the fight, and would lead to less people getting hurt in the long run.  I didn't like Kaiser's followers, I had zero respect for them, but I didn't want to see them torn apart by Bitch's dogs.



``This territory is ours,'' Bitch growled at them, as people backed away.  Brutus, Judas and Angelica were larger now, their skin split with bloody spikes of bone sticking out of the gaps.  ``Leave.''



``Kaiser will hear about this!'' the bottle man shouted.



``Leave!'' Bitch shouted.



Tom, still mindless with pain and fear, jumped at that command.  He tried to pull himself to his feet and failed, falling to the ground again with a ragged scream.  When he reached out, imploring his friends for help, the skin of his hands and face were almost completely covered in bugs and blood.  It did a lot to help spook the rest into a retreat.  Most of them fled.



The bottle man cautiously moved forward to Tom's side.  I didn't move from where I stood/crouched as he bent down to help Tom stand and limp away.



``Fuck,'' Bitch muttered.



``I'm sorry,'' I said, ``I hope I didn't do anything wrong by stepping in.''



She shook her head.



``I mean, maybe if I hadn't come out, it wouldn't have gotten violent.''



``He was working up the courage to shoot me,'' she spoke.  ``It's fine.''



``What are you going to do?''



``What?''



``I mean, they're going to come again.  Maybe soon.  Depending on what they say or who they complain to, there might be people with powers the next time around.''



``I'll manage.''



``I know this is your space, I think it's perfect, but maybe you should consider moving somewhere--''



She gave me a hard look.  ``Do you want to get hit today?''



I shut my mouth.



``I'm going inside to pick up the shit.  You can help, or you can go back.  Doesn't matter to me.''



I looked over my shoulder in the direction the skinheads had retreated.



``I'll help,'' I decided aloud. ``I said I would, and you might need backup if they decide to come back in force.''  Besides, I'd texted Brian to come, and he'd need a proper recap of what had gone on.



She only whistled twice for her dogs to follow her back inside, glancing back to see they were still following.  She looked at me, and I wasn't entirely sure, but I thought maybe she didn't look as angry as she usually did.





