





Brian arrived as Bitch and I were trudging through the field with shovels and trash bags in hand.  Not the image I wanted him to get of me, but I was glad to see him nonetheless.



I'd rinsed off using the tap at the dog's water trough, but I was still covered in dirty paw prints, grass stains, and my skin still itched with the feeling of bugs crawling on me.  I had little doubt that with my wet hair and the state of my clothes, that I looked pretty damn grungy.



``There's bullet holes in the front door,'' Brian spoke from the other side of the chain link fence, raising his voice to be heard over the torrent of barks.  He was wearing his costume and helmet, but had the visor flipped up and he wasn't shrouded in his darkness.  From a distance, he'd look like some guy in motorcycle gear.



``Quiet,'' Bitch ordered, and the dogs fell silent.  Seeing what the other dogs were doing, the few who hadn't learned the command stopped after one or two more barks as well.



``Yeah, they fired off their guns a few times,'' I told him.



``And you're still here,'' he said, in mild disbelief.



``My call,'' Bitch told him.



``It's a bad call,'' he admonished her.



``I'm not leaving.''



Brian folded his arms.  ``Is your pride or stubbornness worth getting those dogs hurt?''



She scowled and looked down at the dogs.



``The thing they said about the hotdogs,'' I spoke, quiet, ``About poisoning your dogs.  You couldn't stop them unless you were here twenty-four seven, and maybe not even then.''



``It's cowardly,'' Bitch spat the words.



``They're cowards,'' I told her.  ``Pretty much the definition of anyone who joins a hate group.  But even if they did take a more direct approach, would you be able to handle it?  Could you deal if twenty people showed up with guns?  Or if Night and Fog dropped by at three in the morning, when it was just you and these guys?''



``I can handle myself.''



I sighed a little and planted my shovel in the ground.  I had to think of a way to convince her.  If I lost my patience in the face of her stubbornness, she would win the argument, and we would all lose.



``I know.  But isn't it better to rely on us?  To actually \emph{handle} this instead of going it alone, hiding and letting those fuckers have the power?''



``I'm not hiding,'' she gave me an angry look.  ``I'm protecting--''



Brian interrupted her, ``Protecting your dogs would mean taking them somewhere safe.''



She shook her head violently.  ``No.  I do that, the fuckers \emph{win.}''



``I've been there,'' I told her.  ``Really, I know what you mean.  But our number one priority is keeping you and those dogs safe.  Once we've handled that, we can focus on dealing with any threats.''



She drummed her fingers against her thigh, looking back toward the building.



``We \emph{are} going to deal with them?'' she made the question a challenge.



``Yes,'' Brian spoke.  ``I don't like that these guys are moving into this area.  I don't like that they'd go so far as to attack a member of our group.  If we don't do something to respond soon, it's going to hurt our rep.  We \emph{need} reputation, it protects us, gives people reason to think twice before they fuck with us.''



Bitch nodded.  ``Okay.''



Brian quirked an eyebrow, ``Okay what?''



``I'll go, and the dogs come with.''



He smiled, ``Good.  I don't think I can hop this fence without getting on the bad side of those dogs, so I'm going to meet you around at the front door.  I'll call Coil on the way''



``Alright,'' I said.  As he turned to leave, I raised my hand in the \emph{lamest} little goodbye wave ever.  Even though I was pretty sure he didn't see it, I was left mentally kicking myself for doing it.



I glanced at Bitch, who was giving me a peculiar look.



``What?'' I asked her, feeling painfully self conscious.



``You like him.''



``N-,'' I started.  Before I went on to protest, I had to stop myself.  Bitch would appreciate straightforwardness and honesty more than anything else.  I wasn't sure I could afford to come across as dishonest or two faced, with her.  ``\ldots{}Yeah.  I do.''



She turned to head back inside.  A horrible thought struck me at that moment.



``Do\ldots do \emph{you} like him?'' I asked her.



She turned her head to give me an angry look, one I couldn't read in the slightest.



``Because if you do,'' I hurried to add, as I started to walk after her, ``Hey, you were here first.  I'll back off and keep my mouth shut if you want to make a move.''



There were about five seconds where she was very quiet.  My pulse pounded in my throat.  Why did I care so much about this?



``You should offer to sleep with him.''



``I-uh, what?'' I stammered.  Relief mixed with embarrassment, and the abrupt change of topic left me struggling to get my thoughts in order.



``It's what guys want.  Tell him you're available if he ever wants to fuck.  He'll accept right away, or he'll start thinking about you as a possibility and he'll take you up on it later.''



``That's-  It's more complicated than that.''



``It's complicated because people \emph{make }it complicated.  Just cut the bullshit and go for it.''



``I don't think you're wrong about there needing to be less expectations and rules and rituals around dating, bullshit, as you put it, but I don't think I can do what you're suggesting.''



``Whatever.''



I realized, belatedly, that she'd actually offered me advice.  As\ldots I struggled to find the word.  As \emph{misdirected} as her suggestion might have been, especially with Brian, it was probably the most blatant gesture of goodwill I had seen from her, next to her telling Armsmaster that she thought I could kick his ass.



``Thank you, though,'' I told her.  ``I'll, uh, I'll keep it in mind.''



``Don't care if you do.''



We crossed the building's interior and Bitch unlocked the door to let Brian inside.  For a second, I thought her bluntness would lead to her telling Brian outright that I liked him, but it wasn't the case.  She was more focused on keeping the more unruly dogs from slipping outside and stopping them from barking at the new visitor than on our discussion.



``I can't get hold of Coil,'' Brian informed us.



``I couldn't get Lisa or Alec, before,'' I replied.  ``You think something's up?''



He nodded, ``Maybe.  You stay here with Rachel.  I'm going to go check on the others.''



``No,'' Bitch spoke.  ``I don't need babysitting, and I'm getting annoyed being badgered by you two.  Taylor goes with you.  I'm going to stay here and pack up.''



``Not a good idea,'' Brian said, with a shake of his head, ``If you get attacked in the meantime--''



``--I have Brutus, Judas and Angelica.  I managed on my own for years, dealt with people tougher than those fuckers.  If there's trouble, I run.''



``And if they take one of your dogs hostage?'' I asked her.  ``One of the ones you can't use your power on, yet?''



A dark look passed over her face as she considered that.  ``Then I run\ldots and I get revenge another day, on my terms.''



Brian tapped his foot for a few seconds.  ``Okay.  If there's trouble, it'll be good to have Taylor at my back.  If and when I get hold of Coil, I'm going to see about getting you some trucks, and people to drive them.  In the meantime, stay alert, and don't get yourself killed.''



Bitch scowled, but she nodded.



``Taylor, we should go.  The sooner we check on Lisa and Alec, the better I'll feel,'' he was already moving as he finished talking.



The moment we were out of earshot, he pulled off his helmet, tucking it under one arm, and asked me, ``What happened?''



I told him, explaining everything after the point Bitch and I heard the ruckus the bottle man and his gang were causing.



``Funny that it's Kaiser that's having trouble controlling his people,'' Brian mused, when I was done.



I wondered if he was still sore over what Kaiser had said at the meeting.



``Coil upped the pressure the moment the truce against the ABB was broken.  I would be surprised if Kaiser didn't have his hands full with that,'' I replied.



``You're defending him?''



It wasn't often that I felt acutely aware of the difference in our skin colors, but being asked if I was making excuses for the white supremacist supervillain was one of those moments.



``I don't want to underestimate him, is all,'' I said.



Brian sighed, ``Yeah.  Maybe you're right.  But Kaiser was willing to demand restitution for the attack on his dogfighting ring, and I'm more than willing to do the same for this attack from his skinheads, if it comes down to it.''



``Both events having something substantial to do with Bitch,'' I noted.



``I'm aware of that fact,'' he told me, frowning.  ``She's useful, she's a credit to the team, but she comes with some problems.  We've dealt with it in the past, we'll deal with it in the future.''



``Right.''



``How was she?  Any fights?''



``Nothing serious.  No, it was actually kind of nice.  I might even do it again, if she let me.''



``Really,'' he replied, skepticism clear in his tone.



``Really.''



``What changed?''



``I'm figuring her out, I think.  How she operates, how she thinks.''



``I've spent ten months on the same team with her, and I haven't even come close to getting how she thinks.  I can usually keep her from going too far or hurting someone, keep her mostly in line and get her to follow directions, but I haven't had a conversation with her yet that didn't make me want to bang my head against a wall.''



``That might be the problem.  You're in charge, she looks up to you, respects you, but\ldots'' I paused.  How could I word this without getting into the particulars of her mode of thinking?  ``\ldots{}But you're something of an authority figure in our group, and her personality demands she tests authority.  Especially when she's insecure.''



Brian considered that.  With a note of approval in his voice, he commented, ``You \emph{have} been giving this some thought.''



``I think that you'd have a much easier time handling her if you took an official leadership role in our group.  Not just being the sorta-kinda leader, but actually taking the position.  If you're not comfortable with that, or if you think the others will make it too hard, well, she'll probably get more comfortable with relying on you as someone in charge over time, as you prove you can handle it.''



``It's been \emph{ten months, }how long does she need?''



``And she's had how many years, without parents, teachers, bosses?  I mean, even when she had foster parents, I don't think it was sunbeams and rainbows, y'know?''



He rubbed his chin.  ``\ldots{}Yeah.''



``Tell me she hasn't gotten at least a bit better in the course of those ten months.''



``Marginally.''



``There you go.  It'll only improve from here on out.''



He offered me a theatric groan in reply.



Brian was walking with long strides, and he had long legs, which forced me to do little jogging spurts to keep up.  It wasn't tiring, I was fit enough from my running, but it was embarrassing to feel like a small child trying to keep up with a grown-up.



Either way, we did make good time getting back to the loft.



Brian put his finger to his lips as he pulled on his helmet and flipped his visor down, emanating his darkness to hide the costume.  I grimaced and brought bugs up to cover my face, calling more from the area to form the beginnings of a swarm.  Brian – Grue now – reached out and coated the front door of the loft in darkness, then opened it without the slightest of creaks or squeals.  Before we ascended the metal stairs leading to the second floor, he coated them in a layer of his power to render our footsteps utterly silent.



I didn't anticipate the scene in the living room of the Loft.



The TV was on, showing ads.  Alec lay on the couch, his feet on the coffee table, a meal on his lap.  Lisa sat on the other couch, laptop resting on her legs, a phone to her ear.  She turned her head as we came upstairs, gave us a funny look, then returned her attention to her laptop.



``Why the \emph{fuck} aren't you answering your phones?'' Grue raised his eerie voice.  He flipped up his visor and banished the darkness around him.



Lisa frowned and held up a finger.  She continued talking into the phone, ``--don't agree with this, and if you'd \emph{asked} me, I would have said you shouldn't do it.  No, yes, I think it's an effective measure.''



She pointed to the laptop, and I stepped forward, moving the bugs off my face and down to the center of my back, where they would be present but not in the way, resting on cloth rather than skin.  I looked at the screen.



``My problem is that it's not just them.  It's their families,'' Lisa spoke into the phone.  ``Unspoken rule, you don't fuck with a cape's family.''



I read the contents of the email she had open.  I felt a ball of dread settle in the pit of my stomach.  I leaned over the back of the couch and put a hand on her shoulder to steady myself as I reached down to press the pagedown key on the laptop.  I read more of the email and then hit the button again to scroll down again.



When I'd read enough of the page to verify my suspicions, I hit the home key to return to the very top of the page.  I checked who else had been CC'ed on the email and the time it had been sent.



``\emph{Fuck},'' I muttered.  ``Fuck!''



Lisa looked up at me, frowned, then spoke to the person on the other end of the phone, ``Can we finish discussing this later?  I've got to talk to my team about this.  Kay.  Later.''



The email was a list.  At the very top of the list was Kaiser.  Following his entry were his lieutenants, Purity, Hookwolf and Krieg, and the rest of the members of Empire Eighty Eight.  It wasn't even limited to people with powers, noting some powerless captains and even some of the lower level flunkies.



The list included pictures and text.  Beneath each of the villain's names was a comprehensive block of data, noting their civilian names in full, professions, addresses, phone numbers, the dates they moved to the city and the first appearances of their costumed identities in Brockton Bay.  There were pictures of them in costume paired with pictures of their alleged civilian identities, roughly matched in angle and size for easy comparison.  Most of the entries had zip files attached, doubtless with more data and evidence.



Kaiser.  Max Anders, president and chief executive officer of Medhall Corporation, a pharmaceuticals company based in Brockton Bay.  Father of a Theodore Richard Anders and an Aster Klara Anders.  Twice divorced, currently living in a penthouse apartment downtown.  Drives a black BMW.  Native born to Brockton Bay, son of Richard Anders.  Richard Anders, according to the email, was Allfather, the founder of Empire Eighty Eight.  From the pictures, it was clear to see how the armor fit around his face and body, how both Kaiser and Max Anders had the same height and body type.



There were other images as well, showing Max Anders with a gorgeous twenty-something blonde, and Max Anders with an older brunette woman at a coffee shop, their table strewn with what looked like paperwork.  I scrolled down to confirm my suspicions, the blonde appeared in another picture with her twin sister.  \emph{Fenja and Menja}.



The brunette woman was Purity, according to the email.  Far mousier than I might have thought, given the sheer presence she had in costume.  Real name, Kayden Anders.  Interior decorator.  Single mother of one Aster Anders.  Purity was promoted to Kaiser's second in command in the same week that Kayden Russel took Max's hand in marriage to become Kayden Anders.  Their separation occurred within the same time period as Purity leaving Empire Eighty Eight to apparently strike out on her own.  Little citations pointed to files apparently in the attached zip file.



Krieg was alleged to be a James Fliescher.  Head of a pharmacy chain, in turn connected to Medhall.  Father of three, married.  According to the notes in his block of information, he took a vacation twice a year with his family.  The email stated that the zip file had copies of inter-company emails where he'd told his coworkers he went to places like South America or Paris, and flight records showed that he was lying.  He\emph{ always} went to London.  Twice a year, every year, for nearly twenty years.  Not once, during these trips, had Krieg been seen in Brockton Bay.



The list went on.  And on.



Every piece of information connected to others.  Even the info on the mooks like the ones I had met earlier with Kaiser's business, showing how they were employed as low level employees of Medhall and its derivative businesses.  It seemed like everyone had a criminal record except the people at the top.



In short, It was comprehensive enough it would take a special kind of willful ignorance to not buy into what the email was selling.



The email had been sent not only to Lisa, but to the Brockton Bay Bulletin, a half dozen other local news stations, and several national ones.  Everyone that mattered, and a few that didn't.



The email had been sent at 1:27 pm this afternoon.  Less than an hour ago.  That was the really bad news.



``Coil did this?''  I murmured.



Lisa nodded, tightly, ``Yup.''



``With your help, I'm guessing?''



``Only a little.  He asked me a few times, to give him my thoughts on some stuff, put him on the right path, eliminate possibilities.  I didn't think he'd get this far, or \emph{go} this far.  Once I got him on the right track, he apparently used private investigators and hackers to dig up the rest of this and get the photographic evidence.''



``Fuck,'' I muttered.



``I don't agree with it,'' she said.  ``It's crossing a line.  It's not just messing with the enemy, there's going to be a ton of collateral damage.''



``Why weren't you answering your phone?'' Brian changed the subject.



She blinked a few times, startled, ``My phone was nearly a goner, so I grabbed a fresh disposable to talk to the boss.  I didn't want to use the phone with the rest of your contact info in it, just to be safe.  Alec was with me the entire time.  He should've gotten any calls.''



``Check your phone, Alec'' Brian spoke, terse.



Alec did.  His eyes went wide, ``Oh fuck.''



``Part of being a member of this team is being on call if we need you.  I swear,'' Brian growled at Alec, ``I'm going to kick your ass so hard--''



Lisa looked from Brian to Alec to me, ``Something happened.  Is anyone hurt?''



``Yes, something happened, no, nobody's hurt.  That's really not what concerns me,'' I told her.  I pointed to the screen, ``Did Coil plan this?  Is this a scheme of his, him using his power?  Using his destiny manipulation or whatever to create some general coincidence, put us in a bad spot, and force us to join him?''



Lisa shook her head forcefully, ``I didn't get the sense of anything like that, and that's not how his power operates.  Besides, he expected we would agree anyways.  He wouldn't jeopardize that with a gambit like this.  It's too crude.''



``So it was just him attacking Empire Eighty Eight on a new front, and a fucking bad coincidence for us,'' I said, as much to myself as anyone else.



``What's going on?'' Alec asked.



I took a deep breath and tried to explain just how bad the situation was.  ``Coil just made a big play against the Empire, and it looks like it was anonymous.  Bitch and I got in a fight with some of his underlings at almost the same time.''



``I don't--'' Alec started.



``Look at it this way,'' I interrupted, ``Kaiser and \emph{every single one}\emph{of his twenty-ish superpowered flunkies }are going to be pissed enough to want to kill someone, after Coil went and turned their lives upside down.  Kaiser and his people know who we are, from our cooperation against the ABB.  Specifically, they know who Lisa is.  So who are they going to blame for this, if not the group his people were just fighting with this very afternoon, the group with the very talented information gatherer in their ranks?''



``Oh.''  Alec said.  ``Fuck.''



``Exactly.''





