





``It's too dangerous to stay here,'' Brian spoke.



``What?'' Lisa and I asked him, almost simultaneously.



``They've got too many heavy hitters and they have absolutely no reason to hold back anymore.  After the ABB thing and the issue with Bitch earlier today, with the number of powered individuals they've got at their disposal, they can probably figure out our general location and go on the offensive.  We can't afford to still be here if they decide to try and root us out or if they lay siege to the Docks.''



``So, what, we run?'' Alec asked.



``Tactical retreat.  Just to be safe,'' Brian stated, his voice firm, ``In case Empire Eighty Eight does decide to organize and come after us in force''



I spoke up, ``Even if they don't blame us for this email that's outing them, secret identity-wise, I'm betting there's going to be more than a few that just want to hurt someone and vent their anger\ldots and we \emph{did} just get in a fight with their people.  It makes us an easy target.  I'm with Brian.  I think we should lay low, at least for now.''



``Okay,'' Lisa said, ``I'm not sure I agree, but I don't see any harm in it.  You guys think you can convince Rachel?''



``Already did,'' Brian said, ``More or less.  She's packing up at her personal dog shelter, and she'll be ready to go the moment transportation arrives.  Lisa, first thing, I want you to get on the phone with Coil.  Get that transportation – I'll text you directions to the place – and get Coil to make a statement, have him make it \emph{damn} clear to Empire Eighty Eight that he's responsible for this email.''



``I don't think he'll be willing, as far as `fessing up.''



``Tell him that I'm not going to sign any deal with him if he can't own up to this and get the heat off us, when we weren't informed and we didn't agree to taking this kind of action.''



Lisa frowned, ``Okay.''



``If he's as clever as he acts like he is, he'll find some angle to make it work.''



``Alright.  I'll try.  What else?''



``Take Alec and find a place to stay with Rachel and the dogs.  I think Bitch has more than one shelter like the one I saw today.  If none of those places work, ask Coil for a place.''



Lisa nodded, ``Okay.  What are you doing?''



``Taylor and I will stay at my apartment.  It's out of the way, and so long as we don't go out in costume, we shouldn't run into trouble.''



I'd be staying at his apartment?  I could remember the tension from the last time I'd been there alone with him, just how aware I'd been of his presence.  The idea of going there to stay \emph{overnight} forced me to focus very carefully on keeping my expression impassive and my hands from fidgeting.  I was glad for the distraction of Alec's response.



``The fuck?'' Alec spoke, ``You're telling us to get out of here, stay in some random place with a bunch of stray dogs, while you go home and kick back?''



``Do \emph{not} get on my case right now, Alec,'' Brian pointed a finger at Alec, ``As a member of our group, you agreed to answer your fucking phone when it goes off.  I'm not much happier with Lisa, for not having a phone ready, but you're the one I'm really pissed at.  From what I heard, if things had gone a little differently, one or both of your teammates could be dead.  Because you guys weren't able to back them up when Taylor asked for it.''



Alec's eyes narrowed, but he didn't reply.



Brian's voice was low, his tone controlled.  ``I'm angry enough that you should count it as a good thing that you're not staying at my place and having to put up with me.  That's why you're not coming with me.  I also need a level head with you and Rachel, and that means Lisa goes with you two.  I'd leave Taylor instead, but I'd rather spread out the firepower between our two teams.''



``Whatever,'' Alec looked back to the TV.  ``Forget I mentioned anything.''



Before Brian could get on Alec's case again, I cut in to ask, ``Shouldn't we all maybe stay together?''



``No,'' Lisa answered me, ``Brian has the right idea.  Together, as a group of five, we might draw attention from anyone keeping an eye out for our team.  Especially if there's dogs around.  Having two teams means we can mount a rescue or provide a distraction if one group gets in a bad spot.''



``Keep your phones on and answer them if anyone calls.  We take turns checking in on each other, every half hour, using the same passwords as before.'' Brian instructed.



``Got it,'' Lisa replied.



``If you \emph{really} can't find a place to stay, and the dogs are safely put away somewhere, you can stay at my place.  You'd be crashing on the couch and the floor, though.''



Lisa nodded.



``Hey,'' I spoke up, hesitant, ``Can I take five minutes to grab a shower and change while you guys hash out the rest of the details?''



Brian made a pained face, but he nodded, ``Go.''



Grateful, I hurried to the bathroom, stopping by my room to grab my costume, a fresh outfit, and my towel.



The shower was being more uncooperative than usual, and I didn't have the time to wait for it to decide to give me warm water, so I jumped in and endured the chilled water just long enough to rinse myself off, scrub the priority areas and get my hair wet.



I cranked the shower off, squeegeed the water off myself with my index finger and thumb, then hopped out of the shower to towel dry and run a brush through my hair.



When I was dry enough, I pulled on a pair of stretch shorts and then started to pull my costume on.  Given that it was all one piece, barring the mask, belt and armor panels, I couldn't quite wear it under clothing without having to wear gloves and long sleeves.  That kind of clothing wasn't an option as the weather got warmer.



One option I \emph{did} have, what I'd been ruminating on, after having my bugs crawl all over me to keep my identity concealed, was only putting it on partway. When the lower half of the costume was on, I folded the top half around at the waist, tying the arms together around me, like a belt.  I put on jeans and a black and red spaghetti strap top that left some of my midriff exposed.  To finish, I tied a sweatshirt around my waist, positioning it over where I'd tied the upper half of my costume.



I sized myself up in the mirror.  The material was fairly thin and it stretched, so it didn't make me look bulkier.  I'd have to see how comfortable the soles I'd built into the foot portion of the costume were inside shoes, but that was something I could adjust.  Having the main part of the body pulled around behind my back meant I could hide the bulkier portion under the sweatshirt.  So long as I didn't untie the sweatshirt where anyone could see, I was golden.



I hurried out of the bathroom, grabbed enough tops, underwear and socks to last me a few days.  I rolled them up to make them compact, and stashed them in my backpack around the armor for my costume, my weapons, the rest of my utility compartment stuff, two books and six hundred bucks in cash.  I slung the bag over one shoulder.  Heavy, but manageable.



I left my room to rejoin Brian, tying my damp hair into a loose ponytail with an elastic while I walked.  I paused for just a second to extend one leg, toe down to touch the ground, so a collection of beetles, roaches and spiders could crawl up my leg.  They settled between my costume and my clothes.



I could deal with bugs being on me, so long as they weren't directly on my \emph{skin}.



``Ready?'' I asked Brian.



He nodded.  He'd pulled off the leather jacket and had it in a gym bag with his helmet.  He was wearing a guy's tank top, beige, leaving his arms and shoulders exposed.  His skin glittered with the tiniest droplets of sweat, from wearing a jacket in the warm weather.



I pulled my eyes away before my attention could draw notice.  I told Lisa, ``We'll see you guys later.''



``Have fun,'' she grinned.



Brian led the way outside, and again, I paused at the door's threshold to collect some more bugs under my clothing and in my bag while I could still be discreet about it.  It wasn't a lot, but it was something.



He seemed to be deep in thought, and there was good cause for that, so I didn't bother him as we walked to the bus stop.



``Am I being paranoid?'' he asked me, as we arrived.



``I'm not the person to ask.  As far as I'm concerned, when you're talking about capes, you can't take too many precautions.  Especially with a group as influential as Empire Eighty Eight.''



``I'll rephrase the question then.  Do you think the others will think I'm being paranoid?''



``Honestly?  Probably.''



``Damn it.''



Our conversation stalled when more people joined us at the bus stop.



``I just realized,'' Brian spoke, ``I never asked if you even wanted to stay over.''



I looked up at him.  I wasn't sure how to answer without conveying my full feelings on the subject.  \emph{Keep it simple}.  ``I do.  It's totally fine.''



``After I was first introduced to the others, I did that a lot.  The guys complained about it, and my sister's mentioned it too.  I take charge, make calls.''



``Really, it's cool.  It makes sense, given\ldots'' I paused, keeping the civilians that were in earshot in mind.  ``\ldots{}the situation, and I like your apartment, so I don't mind staying there.''



``Yeah?''



``Definitely.  Hell, I'd have you decorate my apartment when I got a place of my own.''



He chuckled, ``I'll do that for you if you make me that outfit we talked about before.''



The costume.  I'd almost forgotten.



``Thanks for reminding me about that.  It sort of slipped my mind.''



``Considering it?''



``Yeah.  Maybe.  It's a big job, but I guess I have more free time now, and, uh, yeah.  That's pretty much it.  I could maybe do it, sure.''  Obviously, I couldn't and wouldn't mention the fact that my decision to ally myself with the Undersiders for real was a factor.



``Yeah?  I'd owe you.''



``Gives us something to talk about while I'm staying over, too.''



``I don't think we'll lack for conversation topics,'' he smiled at me.  That boyish smile that I'd noticed on day one.  If I was being honest, I would even say it was tied with his voice for the thing I liked most about him, aesthetically.  It was maybe unfair to think so, but I generally saw the vast majority of teenage boys as awkward people that combined the traits of a child and an adult in the most unfortunate ways possible.  Brian was the opposite, and it was his voice and his smile that really nailed the effect.



I felt my ears warming up in the telltale sign of an incoming blush and looked away, distracting myself with an exhaustive investigation of a brown paper bag by the side of the road.  If I kept on that particular line of thinking about Brian's better qualities, I was guaranteed to wind up saying or doing something to embarrass myself.



The bus arrived and we climbed on.  I flashed my school ID, while Brian paid with tickets.  I found an empty seat, and Brian stood next to me, holding the pole.  He was close enough to me that his leg pressed against my arm.  Even though I could have moved my arm away, I left it where it was.



I wasn't the sort of girl Brian would be attracted to.  I knew that.  I could settle for just his presence and friendship.  I could enjoy it if there happened to be casual body contact between us, even if it was a bit pervy.



Our brief conversation had let me relax and start to enjoy the possibility of an evening in Brian's company, but what I saw next was a bucket of cold water in the face.



The bus had stopped to pick up passengers, and Sophia Hess was among them.  Her sleeveless polo top was long, extending down to her waist, and clung tight to a slender body with curves and a chest I'd never have.  The tennis skirt she was wearing was only barely long enough to be decent.  More than one set of eyes turned her way as she boarded the bus, Brian's among them.



She was oblivious to the attention and to my existence, preoccupied with a conversation over the phone.  She looked annoyed, bored, and distracted, as the person on the other end did most of the talking.  Probably a parent.



The bus continued on its route, more people filed in, and the people near the front moved further back.  I stared at her, waiting for the moment she would see me and make eye contact.  I wasn't sure what she'd do, or what I'd do, but that moment held every iota of my focus.



She was Emma's best friend.  The person who had shoved me into the locker, back on the day I'd gotten my powers.  On countless occasions, she had pushed and tripped me, often several times a day.  She'd knocked me down the stairs, when I was near the bottom of the flight, even got others to do similar things.  Given that she'd been suspended after my last meeting with her, I somehow didn't think she'd walk away without confrontation if she saw me.



My leg bounced restlessly.  Without thinking about it, I'd readied myself to leap out of my seat, to defend myself, get out of the way, or respond to whatever happened.  My thoughts looped through possible things she might do, things I might say or do in response.



Sophia put the phone away, and gazed out the window for a moment.  When she'd seen everything there was to see of transition point between the Docks and Downtown, she glanced over the bus' interior.  Her eyes paused on advertisements running along the top of the bus, then settled on Brian.



The appraising look she gave him was unmistakable.  It lingered long enough that it probably would have been uncomfortable for him, if he'd been aware of it.



Or maybe not.  Maybe he would've liked the attention from a girl that looked like her.



Bleh.



She still hadn't seen me.  I could see why – I was sitting, and she and Brian were standing, and there were others between us, obscuring her line of sight to me.



I startled when something moved to my left.  It was just the person sitting next to me standing to get off at the next stop, but it made me aware of just how tense I was.  I reached up and touched Brian's elbow.  When he glanced down, I moved over into the empty seat and pointed to the vacated spot.



He smiled and sat down beside me.



My pulse was pounding in my throat, and I couldn't tell him why, not here.  I waited and tried to organize my thoughts, as people from the front of the bus moved toward the back.  It took some doing, but I avoided looking at Sophia.



I reached up and put a hand on his shoulder, used it to rise high enough to murmur in his ear, ``Do me a megahuge favor?  I'll explain after.''



``Of course,'' his voice was barely audible over the noise of the bus.  He turned his head just enough to look me in the eye, and my heart skipped a beat.



``Just play along.''  I put two fingers on the side of his chin, turning his head, and rose out of my seat just enough to touch my lips to his.



I expected electricity, fireworks, all that stuff you hear about.  I thought my heartbeat might race, or that my thoughts might dissolve into that chaotic mess that I'd experienced a few times in the recent pass.



What I didn't expect was the calm.  The tension melted out of me, and all the worries, anxieties and conflicting thoughts faded into the background.  It was like the sense of peace I got from waking up at the loft, times ten.  All I thought about was the contact, how nice it was, the feeling of his lips on mine.



I broke the kiss and looked him in the eyes as I settled back in my seat.  Even before he opened his mouth to say something, I was giving him the smallest shake of my head.  He closed his mouth.



When I looked away, I felt his arm settle around my shoulders.



I looked and didn't see Sophia at the front of the bus.  When I checked over my shoulder, I found her near the back.  She was staring at me.



I imagined it wasn't so different from that primal sense of satisfaction Bitch had felt when she'd set the dogs on me.  Except where Bitch had lorded it over me with a smug smile, I didn't change my expression from the light smile that was already on my face.  I gave Sophia a moment's eye contact and nothing more, before turning to face the front of the bus once more.  She wasn't worth it, wasn't worth spoiling this.



I avoided looking back to see what she was doing or checking if she was still there.  When Brian asked me if I minded stopping to go shopping before we went to his apartment, I nodded.



I had taken Lisa's advice, trying to improvise, be more impulsive.  I had also done as Bitch had suggested.  I'd let Brian know I was interested, kind of.  Not to the extent she'd suggested, but it was something.  Definitely something.



Except I'd just forced matters with Brian, and now I not only had to explain, but I had to deal with a night of awkwardness in his company, on top of the threat of action from Empire Eighty Eight.





