





``So, about that `favor' I just did you\ldots'' Brian began.



I glanced around at the other people who were departing the bus, still more were waiting at the stop.  ``Can we talk about it later?  In private?''



He gave me a curious look, but he replied, ``Of course.''



I knew I was making it worse by procrastinating, that I'd only get more awkward if I dwelled on it.  Whether I admitted my feelings or told him about Sophia, both felt too personal to talk about with the crowd of strangers following us off the bus.



We'd gotten off the bus at a mall I'd never been to.  It wasn't one of the ones with any major chains or stores in it, but it wasn't small enough to deserve the label of `strip mall' either.  There were more people milling around than I thought there might be, given that it was still mid afternoon; high school students and nine to five employees wouldn't be out yet.  I realized there were more than a few people in their late teens or early twenties with backpacks and bags.  College students.



``Next bus going by my place should come in half an hour, but we can stay longer, if you want,'' Brian told me.



``What did you want to get?'' I asked him.



``Bus tickets and some stuff for breakfast.  This is the closest spot to my apartment that has both.''



``Okay.''



``You need anything?''



``Toothbrush, toothpaste, and I was thinking about grabbing a book.''



``Don't worry about the toothbrush or toothpaste, I have extra stuff set aside for Aisha when she comes, and replacing that before then is easy.  Want to go to the bookstore, and I'll meet you there when I've got what I need?''



``Sure.''



That might have been the point we went our separate ways, but the grocery store and bookstores were in the same direction.  We walked together, in awkward silence, until we saw a crowd outside a store.



It was an electronics store, with computers and TVs in the window.  The number of people had reached critical mass and was drawing more onlookers, to the point where it was hard to find an angle where we could see the screens.  At least, where \emph{I} could see the screens – Brian was tall enough to see over the average person.



The images displayed on the screen were the same as the ones I had seen in the email, earlier.  Max Anders and Kaiser.  Kayden Anders and Purity.  The blondes as Fenja and Menja.  The broadcast flickered through all of them: Hookwolf, Krieg, Night, Fog, Stormtiger, Othala, Cricket, Rune, Victor, Alabaster, the Crusader\ldots the list went on.  The screen shifted to two news broadcasters.  In the top right corner of the screen, there was the usual story of the moment image, showing Max Anders sitting at a table at some event, with a swastika followed by a question mark hovering above him.



``Word's out,'' Brian spoke to me, quiet.  ``If they didn't know about this already, they do now.''



I nodded without turning away from the screen.  The broadcast changed to show Armsmaster and Miss Militia with a man in a suit and tie, addressing a crowd of reporters.



``We're probably not going to see anything new here,'' Brian whispered to me, ``And we can't hear anything through the window.  We'll text Lisa, let her know it's on the news, and she can handle the information side of things.''



I nodded and joined Brian in walking away.



``It's clever,'' I murmured, glancing around to ensure nobody was in immediate earshot, ``I don't know if I agree with how the boss went about it, I think it sort of crosses a line, but I can see the reasoning.  Controlled chaos, keeping everyone that matters busy and off-balance so he can advance his own agenda.''



``It \emph{does} cross a line, yeah.  We'll have to see how that works out.''



I saw the bookstore to my left, ``I guess this is where we part ways?''



``Sure.  I'll meet you in a couple of minutes.''



Being around Brian was tense, in a way.  I found most social situations awkward, and the only way I could cope was by planning out what I'd say, considering and anticipating everything in advance.  Around Brian, though, I got so flustered and distracted that I couldn't do that.  That led to me feeling like I sounded dumb, created awkward pauses.  It only got worse as I became aware of any of it.  That was where the kiss had been so nice, settling my thoughts and giving me a sense of tranquility for that all too brief moment.



Except things were worse now, and Brian and I had a discussion looming.  Worse, I'd been so focused on not screwing up the dialogue \emph{now}, in the present, that I hadn't had time to think about what I'd say in the immediate future.



In short, as much as I liked his company, liked \emph{him}, I was glad for the break and the chance to calm down and get my thoughts sorted, so I could handle it when the conversation happened.



The used bookstore wasn't organized in the slightest.  There was a heavy musty smell, and the racks were organized haphazardly.  There were fantasy books and science fiction both classified under `fantasy', which irked me, and non fiction was one broad category that took up an entire wall.  If there was a system to sort the books, I couldn't see it, and many of the shelves had books on their sides, stacked atop one another, sometimes two or three layers deep.  Some of the fuller shelves had books stacked on the ground in front of them, requiring careful steps to avoid knocking anything over or stepping on a stray book.



The sole occupant of the store was an elderly black man that sat behind the counter, leaning back in a chair with his hands folded on his stomach.  The television played a little too loudly for the store's old school atmosphere.  Some courtroom show.



After checking out the selection of fantasy books in the middle of the store, I navigated my way to the back, keeping an eye on the signs identifying each section.  The Romance section had way too many books in it.  So did Mystery, as far as I was concerned.  Both genres tended to be a little too repetitive and samey for my tastes.



As I disappeared behind a row of shelves, the man at the counter called out, gruff, ``Don't be shoplifting because you think I'm not paying attention!''



``Alright!'' I called back, feeling silly as I said it.  I wasn't sure how else to respond.



I found the Instructional section and spotted the item I'd come into the store for in one of the stacks on a lower shelf.  Dog Psychology: The Basis of Dog Training.



With minimal experience being around dogs, I needed more information, if I was going to continue relating with Bitch.  I'd known I wanted a book on the topic of how dogs thought and related to others, and I was glad to have found it.



I tucked the book under one arm, then picked up another book on tailoring, as a possible reference for future costume design.  Flipping through it, I wasn't too impressed.  I checked out another.



My thoughts froze as a hand touched my hair.  I belatedly remembered Brian.  I tried and failed to organize my thoughts.  I'd forgotten to plan out what to say to him, and what would he be doing touching my hair?



I started to turn around, only for the hand to seize my ear and wrench it hard enough to make my legs buckle at the pain.  I was shoved over and my body's weight and momentum weren't enough to pull my ear free from my attacker's grip, with the skin joining my ear to my head paying the price.  I felt like my skin was tearing, and I couldn't even scream as my breath hitched in my throat.



I collapsed on top of a pile of books, and the white-hot pain surrounding my ear was so overwhelming I wasn't entirely sure if my ear was still being held or not.  A knee pressed against my side with enough force I had little doubt that most or all of my attacker's body weight was on top of me.  Long fingernails stabbed into my cheek, forcing the skin in between and against my teeth, as my assailant gripped the side of my jaw.  It not only forced my mouth painfully open with the pressure of my cheek against my own teeth, but it pressed my face hard against the pile of books beneath me.   My cry of protest was reduced to an incomprehensible, muffled noise, which became a primal groan as my ear was twisted again, the opposite direction as before.



``Something you should know about me,'' Sophia's voice was dulcet, ``The reason I'm such a good runner?  It's not that I'm driven to win.  It's that I really, really hate losing.''



She wrenched my ear again, changing the direction again, and I cried out.  If she went any further, I was positive the skin would tear and the ear would come off entirely.  I struggled, but the books slid beneath my hands and knees, giving me minimal traction.



``And I hate losing the most when it's to a depressing queef like you,'' she rocked her right hand back and forth against my cheek, as if she wanted to drive her fingernails through the skin.  Her thumbnail bit into the underside of my jaw.



\emph{I have bugs inside my jeans and backpack.  I can end this.}



With both hands, using her grip on my ear and jaw, she lifted my head up and plunged it down hard against the pile of books beneath me.  It wasn't the worst hit I'd ever taken, but it still left me reeling.



I couldn't afford to take too many hits to my head.  Though my concussion was more or less healed, I'd be susceptible to a relapse of symptoms and future concussions for a while yet.  I just had to use my bugs to get her off me, buy myself time to get my knife and baton and\ldots



\ldots{}and then I'd be fucked.  I'd do more damage to myself in the long run, outing myself as the girl with the bug powers.  I'd never be able to go home to my dad.



Sophia let go of my cheek to cover my mouth with her hand.  Using this fresh hold, she wrenched my head as far to the right as it would go, so I could see her looming over me, her hair hanging down around her face.  She looked like a panther, black-skinned, savage, teeth bared just a little as she panted.



She let go of my ear and tapped hard against the lens of my glasses as she continued, ``This is your reminder that everyone has their place in life, Hebert, and you should \emph{stick to yours}.  Trying to act better than you are only embarrasses you and irritates me, get it?''



She yanked on my ear again, as if to make her point clear.



``Nod if you understand, and I'll let you run off home.''



I glared up at her.



My fingertips traced against the books on the bottom shelf until I found the hardcovers.  I got hold of one, pulled it free, and in the same motion, drove one of the corners of the text into Sophia's side.



She fell over, and I flipped onto my back to swing again, switching to a two-handed grip to add more power to the swing.  The time it had taken me to get into position for another swing, however, bought Sophia time to get out of the way.  I had Brian's tips on fighting in mind, keeping on the offensive, and the only way to do that was to fling the hardcovered reference book at her head.  She used her arms to knock it out of the air, then winced, rubbing her arm.



``What the fuck is your derangement?!'' I shouted at her.  ``In what twisted perspective is it all right to stalk and attack someone because they kissed a boy?''



``It's not just that,'' Sophia started toward me, then stopped when I let my backpack fall to the ground and straightened, ready for another confrontation.  ``You got me fucking suspended.  I don't care about missing class, but I'm off the track team until further notice.  And it's all because you ran off to whimper for the grown-ups.  I need that shit.''



``Boo fucking hoo.  If I knew it mattered that much to you, I'd have written a letter to your coach days ago, just to drive the point home and make sure you never got back on the team.''



Sophia gave me a look of pure loathing, ``You're a coward, Hebert.  A rat.  You know you're a nerd, you're flat chested, scrawny.  Nobody likes you, nobody wants you for a friend, you're not good at anything.  So you run, you hide, skip school, stay quiet, don't do anything with your waste of a life.  And if things get tough, if anyone decides to have a little fun at your expense, you go crying to the people in charge, because you can't take it.''



My ear throbbed.  I put my hand up to tenderly touch the base of it, and pulled away when I felt a bitter stinging pain in response.  My fingertips were red with blood when I lowered them.



``FYI, it was Emma's dad who called the meeting at the school, not me,'' I replied without anger in my voice.  I was sobered by the sight of my own blood.  Odd as it sounded, I felt more comfortable with the situation.  I'd dealt with more serious fights, and I felt like I could handle this better, having seen the blood, knowing the ante was higher.



``You still told \emph{someone}.''



``So what if I did?  What did you expect, that I'd keep my mouth shut, put up with it?''



``That's \emph{exactly} what I expected.  It seems you didn't get my point about knowing your place.''  Her eyes flickered to the spot where she'd just held me down.  ``Maybe you'll get the message after round two.''



She started toward me, and I had a good sense of how this would go.  She was my height, but she was a stronger than me, with more room for muscle on her frame.  Not that she was fat, or heavy in any way, but her physique was athletic, slender, and mine was that of a scarecrow – just plain thin.



There was also the broader context – I was already hurting, and she was \emph{fucking psycho}.  If it came down to it, I suspected I'd get the worst of it in the fight, unless I either found a way to get to my weapons in my bag or used my powers.  That didn't mean I wouldn't be able to do some damage to her in the meantime, it just meant she'd kick my ass in the process.



If that was how it turned out, I was okay with that.



``Enough,'' the male voice cut in.



Sophia halted in her advance.  She turned an impassive expression to Brian, who stood to her left.  He set plastic bags of food on the ground as she watched.  ``The boyfriend.''



Brian looked at me, and there was a touch of concern in the expression.



I turned my attention back to her.  ``Meet Sophia.  One of the girls that's been giving me a hard time at school.''



The look of concern disappeared from his face in an instant.  It was replaced by anger.



``She's lying,'' Sophia told him, without the slightest trace of hesitation. ``She cheated off me for a test, and got us both suspended and-''



``Shut up,'' Brian's voice was low, not much different from his normal speech, but Sophia got the message.  She closed her mouth.  He turned to me, ``Are you okay?''



``My ear hurts like hell, and I don't even know what she did to the side of my face, but I'm alive.''



``Good.''



Sophia bolted, and there were only two ways to go – through me, or past Brian.  She chose the easy road, dashing toward me, and I lunged for her, aiming to grab her, slow her down enough for Brian to step in.



Except she was faster than I'd anticipated, proving her position on the track team wasn't just for show, and even my last-ditch effort at grabbing her wrist fell short.



Brian and I gave chase, and were stopped when the guy from the front counter emerged and stepped partway between us and Sophia.



``What's this?'' he looked between us.  Behind him, Sophia turned to face us, assessed the situation and then backed up a few steps with the old man's back was turned to her.



``She attacked me,'' I said.



``Looks that way, sure, but the girl said it was justified, that you stole something from her on the bus.  Asked me to stay at the counter and turn up the volume on my show while she got it back.''



``It's a lie,'' I told him.



The old man ignored me.  He looked at Brian, ``I thought you'd be on the other girl's side, not sure I would've let you past if I knew it was any different.''



Why had he come to that conclusion?  Because Brian and Sophia were both black?  I didn't like that assumption, that I was automatically the bad guy, here.



``No,'' was Brian's curt reply.  ``My friend is right.  That girl attacked her.''



Sophia backed away another few small steps, behind the old man.  When Brian moved forward, the old man got in his way, angry.  ``Hey now, I'm not going to have any more fighting in my bookstore.''



Sophia saw her chance and ran.  I raised my hand, as if I could somehow reach out and stop her, then dropped it.



It took us another two minutes to wrap things up with the old man.  He accused me twice more of being a thief and gave us a dressing down for causing violence in his store.  When he started demanding we go to the back with him and talk about the damage and mess, Brian grabbed my arm and guided me out of the store, ignoring the old guy's insults and shouts of protest.  We took the quickest route out of the mall and started walking down the street.



I'd left the dog psychology book behind, I realized.  That bummed me out as much as anything.  I hadn't really won or lost, as I saw it.  Any injuries I'd sustained were balanced out by the fact that I'd fought back, and that Brian had been there to back me up.



Well, that was my gut feeling, anyway.  It was entirely possible that I'd change my mind after I saw how bad the damage was to my face and ear.



Might as well know sooner than later.  I gestured to the side of my head and asked Brian, ``How bad is it?''



``I think that ear's going to need stitches,'' Brian told me.  ``You've got a tear in the skin by the earlobe.''



I nodded, mute.



``You want to press assault charges?''



I shook my head.  No money to do it, no use in trying.  She had Emma's dad backing her up, and the only witness was the old guy from the bookstore, who had given me the distinct impression he sided with Sophia over me.



``So that's what you've been dealing with at school?'' he asked.



I shook my head.  When I tried to speak, a surge of emotion made my voice reedy.  It took me a second to figure out how to get the words out, and the end result was that my voice sounded hollow and robotic, ``That was the worst she's tried to hurt me physically.  Guess it's different outside of school.  I can defend myself more, but she has less reason to hold back.''



``So I suppose the,'' he cleared his throat, ``Kiss on the bus?  It was for her benefit?''



I swallowed hard, in an effort to get my voice more normal.  I probably wouldn't get another chance.  ``Some, yeah.  Some was for mine.''



He turned toward me, eyebrows raised a fraction.



I shrugged, doing everything I could to sound more casual than I felt.  I wasn't sure how successful I was.  ``I, um, I like you.  You don't need to make a bigger deal of it than it is, I just-'' I floundered as I tried to find the words, already regretting opening my mouth.



He didn't speak, giving me a chance to continue, ``I think you're good looking, I like you as a person.  I \emph{respect} you, more than any of the others, because you're smart about what you do, career-wise.  You know.  And because you're so comfortable in your own skin, so confident.  I admire that.''



``You sound so analytical,'' Brian offered me a slight smile, but he looked a little pained, ``Going through the points, step by step, like you're checking things off a list.''



``That's not- I'm not trying to.''



``I'm not criticizing you.  I'm saying it seems very \emph{you}.''



``No.  I just thought, um, you've gone out of your way to spend time with me, you were meeting me on my runs, invited me to be at your place alone.  I've noticed maybe there was more casual body contact, and thought it might be intentional, a signal, guy flirting, I dunno.  The present, the amber\ldots'' I trailed off.  It had sounded like a stronger argument in my head than it did out loud.  Except\ldots what was I trying to argue?  Was I trying to convince him he liked me?



``Ah, geez.  I'm sorry if I sent the wrong signals.''



My heart dropped.



``You've got to understand, the only girls I've spent time around are Aisha and Lisa\ldots Bitch doesn't count, you know?''



I nodded, tightly.



``Even when I was attending high school, I was always gone the second classes ended.  Meeting my dad at the gym, working, or going home to plan some costumed burglary or whatever.  You know?  I don't have much experience, being around girls.  I don't really think that much about the relationship thing, outside of noticing when I see a good looking girl.  It's something I always figured I'd get to later, when I wasn't so preoccupied.''



I offered another nod, not trusting myself to open my mouth.



``So if I gave you the wrong impression, I guess it's partially because I have no idea what I'm doing, and because I'm an idiot when it comes to stuff like that.  I don't see you that way.  It's\ldots more like you're my sister, someone I want to protect, and help, and support.  I like you as a friend, I can even see us being best friends, somewhere down the line.''



\emph{Like his sister}.\emph{  A friend}.



``If there was more body contact or if I was spending time with you, or any of that other stuff you mentioned, I promise I wasn't teasing or anything.  If any of it was conscious on my part, it was meant to make you feel more welcome, let you know you've got me around, because I knew you had a rough time of it at school.''



\emph{And pity.  There's the trifecta.  }``It's okay.  You can- you can stop now.''



We walked a few seconds in oppressive silence.



``I'm sorry.  I feel like an asshole.  Like I'm kicking you while you're down.''



I shook my head, ``It's fine.  Not a big deal.  Just drop the subject?''



``Alright.''



I bobbed my head in mutual agreement and swallowed the lump in my throat.  In a different place or situation, if Brian wasn't around, if I had privacy, I might have cried.  I didn't have that luxury, so I focused on putting one foot in front of the other, controlling my breathing, reading street signs and store names, and just focusing on anything that wasn't Brian or the conversation we'd just had.



The walk back to his apartment was long-ish, maybe half an hour, and was peppered with only meaningless small talk and long, wordless pauses.  We got up to his apartment, and he started putting things away and getting the first aid stuff together.  I turned on the TV to liven up the awkward quiet.



I didn't have to wait long before something caught my eye.  It was on channel 4, a live update on the Empire Eighty Eight situation.  From the looks of things, there was no doubt in my mind that Kaiser's people were giving Brockton Bay their response to the email.





