





Purity floated above the docks, an oversize firefly against a blue-gray backdrop of sky.  She came to rest over a building that had been half built and left abandoned, a small crane jutting out of the middle of it.  A building I recognized as Bitch's place.  Her improvised dog shelter.



``Brian!'' I called out.  ``You want to see this!''



The cameraman tried to zoom in and focus on Purity, but only intensified the lens flare effect that followed her.



He zoomed back out just in time to see her take action.



The beams of light that blasted from her palm weren't straight.  There was a bit of a spiral to them, as they formed a rough double helix.  The end result was wider than Purity was tall, tearing into the building to topple the crane against one wall.  She turned the light on the other walls, obliterating them.



It took her less than a minute to level the building and pulverize any part of the structure that stood higher than the sidewalk.



She paused, and hovered there in the midst of the dust and the motes of light that had followed in the wake of her power.  She turned and shot the next-closest building, directing a smaller, tighter beam at one corner where the structure met the ground.  She hit the next corner, then swept the oscillating shaft of light through the ground floor to obliterate any supports that stood within.  The building toppled messily with brick walls sloughing off and cresting plumes of dust.



The building hadn't even finished falling down before she started work on the next two, devoting one beam to each.



``Were there people in there?'' I asked, horrified both at the idea and at what this woman was capable of doing. ``What about those other buildings?



Brian was behind his couch, watching, ``There might have been, and there might be.''



My need to hurry overrode my modesty.  I stood and pulled off my top, leaving just my bra on, making sure to keep my back to Brian.   I removed the sweatshirt I had tied around my waist and untied the arms of my costume.



``What are you doing?''



``Getting ready,'' I put my arm through one arm and worked my fingers into the gloves.



Brian walked around the couch and I hurried to raise the top half of my costume and clutch it to my chest, covering myself.  He put his hands on my bare shoulders and exerted enough force to push me back down to a sitting position.  I complied, stiffly, reluctantly.



He pulled his hands away a little more quickly than he might have a day or two ago, jamming them in his pockets.  I hunched my shoulders forward self consciously.



Brian took a deep breath.  ``Not your job.''



``They're doing that because of us,'' I adjusted my grip on my costume top to free a hand so I could point it at the TV.  The cameraman was retreating from the scene, and the image was wobbling as the camera rocked with his movement.  The spark of light that was Purity was moving in his general direction as she leveled more buildings.



``Because of Coil, not us.  The heroes will be the ones to take care of it,'' Brian retorted.



``They could be hurting innocent people.''



``Given who these guys are, I'm pretty sure they've been hurting innocent people for a long time.''



I turned to frown at Brian, ``You know what I mean.  We-''



``Undersiders,'' A female voice cut into the conversation.  ``Protectorate.   Take note.''



Our heads turned back to the television screen.  The camera showed a brilliant glare that could only vaguely be made out as a face.  The view shifted, and I heard her command, ``Hold it.''



The camera steadied and focused on Purity's face, from ground level looking up.  I suspected the cameraman was on the ground.



``You took the most important thing in the world from me,'' her voice was without affect, flat.  ``Until she is returned, this doesn't stop.  I will take this city apart until I find you or you come to stop me.  My subordinates will murder anyone, \emph{everyone}, until the matter is settled.  I don't care if they are genetically pure or not.  If they haven't allied with us already, they missed their chance.''



She bent down to take the camera.  While the image swayed wildly, Purity spoke, ``Night, Fog.  Demonstrate.''



The camera steadied, fixed on a man and a woman in gray and black costumes, respectively, featuring cowls and cloaks.  Behind and to the side of them was an unnaturally pale and white haired young man.



The man in gray evaporated into a rolling cloud of white-gray fog, moving toward the camera.  Purity took flight, moving up and above the scene, keeping the camera focused on the cameraman.  As the camera rose and the view of the scene expanded, I could see Crusader off to one side, leaning against a wall with his arms folded.



As the mist enveloped the cameraman, Night strode forward, disappearing into it.  The timing of what happened was wrong, too soon after she entered the fog.  There was a ragged scream, and then blood sprayed out of the mist to paint the surrounding road in dozens upon dozens of long splashes of crimson.



The fog moved as though it had a mind of its own, congealing into the man once more.  When he had fully pulled himself together again, there were only a few spatters of blood six or so paces from where the body had fallen, and Night, standing in the middle of the road.  No body, no clothes, no blood remained where the fog had passed.



``We are not the ABB,'' Purity spoke, not bothering to turn the camera back to herself, ``We are stronger, both in powers and in numbers.  We have discipline, and thanks to you, we have nothing left to lose.  I will have my daughter back, and we will have our restitution.''



Purity dropped the camera, and the view spun lazily as the camera hurtled to the ground.  There was the briefest of glimpses of the trail of light that marked her departure, before the camera hit the ground and the television went black.  After a moment, the `BB4 News' logo appeared on the screen against a blue background.



``Crap,'' Brian said.



``So.  If you're not going to go after them to save people,'' I wasn't able to keep all the bitterness out of my voice.  ``Maybe you'll do it for our rep, after we got called out like that?''



``That's not- Taylor, I don't want people to get hurt or killed, either.  I'm not a villain that aims to hurt people.  I'm just being practical.''



``You didn't answer my question.  What are we doing now, after hearing that?''



``We're calling Lisa.  Or you are, and I'll take care of your ear while you do it.''



I nodded.  I took the opportunity to get my top back on while he got the first aid kit, and grabbed my cell phone.  Brian used saline and a wet cotton wipe to wipe around my ear, and I dialed Lisa.  She picked up on the first ring.



``Lemon J,'' I told her.



``Bumblebee S,'' she replied.  ``No immediate danger, but the situation doesn't look good?''



``Right,'' I replied.



Brian put the cotton wipe aside.  It was a red-pink with flakes of my dried blood on it.  He prepared another to continue working.



``You see that bit on TV?'' I asked her, ``Hold on, I'm putting you on speaker for Grue.''  I'd used his codename for security's sake.  I fiddled with the keypad to get the phone to speaker mode.



Lisa's voice was tinny through the low quality speaker.  ``Purity?  I saw the bit on TV.  From what I picked up, child protective services and a contingent of capes went into her place and walked out with her baby while she was at work, before she even had a chance to hear about the email.  Mama bear snapped.''



``Tattletale,'' Brian spoke, ``Did you talk to Coil?''



``Coil says he told Kaiser straight up that he was responsible for the emails.  I believe him.  If Purity and Kaiser's other subordinates don't know, Kaiser either hasn't seen fit to tell them or he's intentionally keeping them in the dark.''



``What?  Why would he do that?'' I raised the phone closer to my mouth to ask her.



``It makes a warped sort of sense to me,'' Brian answered for Lisa.  ``He lets his people believe we're responsible, with Purity's group gunning for us and the Protectorate.  Hookwolf hates us anyways, because of Bitch, so he goes along.  Kaiser lets them deal with us, with all that fury and hate and no-holds-barred torture, murder and maiming that comes with blaming us.  When we're dealt with, or when it's convenient, he tells them the truth, turns that bloodthirst against Coil.  His people won't ever be scarier or more vicious than they are right now.  Why not maximize the damage?''



``Doesn't that fall apart if Coil admits, publicly or to the members of Empire Eighty Eight, that he's responsible?''  I asked.



``Yes,'' Lisa's tinny voice replied, ``But Coil won't.  He was willing to talk to Kaiser, fess up to the man himself face to face, but going with a more public route risks putting him in the spotlight, drawing attention to himself, and he's not going to do that.  I suspect Kaiser knows that and is accounting for it.''



``So what's next?'' I asked, ``I think we should do something to step in, but Brian was saying that he thought we should continue to lay low.  Before Purity said her piece, anyways. Not sure if he's changed his mind.''  I gave him a look.



``I haven't,'' Brian spoke, loud enough to be picked up by the phone.  He dabbed ointment on my ear, making me wince.  ``Sorry.''



I wasn't sure if the apology was over his stance in the discussion or the medical care.



``According to the news and my, um, inside source,''  Lisa spoke, referring to her power, ``Purity hasn't stopped.  She's doing strafing runs across the Docks.  She moves too fast for anyone but Dauntless or Velocity to catch, and she hits harder than both of them combined.  She's knocked down four more buildings while we've talked, I'm pretty sure. How long before she happens to knock over our hideout?''



Brian pursed his lips.



``And she leads her own sub-group within Empire Eighty Eight, so I'm betting that Fog, Night, Alabaster and Crusader are on the streets, doing their own thing.  I dunno about you guys, but I have friends in our neighborhood.  I'm very not cool with that.''



Brian sighed, ``Fine.  We go.  But no direct confrontation until we have a game plan, especially not before we reunite our two groups.  Where are you guys?''



``Holed up on the far side of the Trainyard, with the dogs,'' Lisa answered, ``Not a bad spot.  Better than the building Purity tore down.  Don't know why she was set up there instead of here.''



I heard a voice on the other end that was probably Bitch's, though I couldn't make out the words.



``So.  We meet?'' Lisa asked.



``We meet,'' Brian replied.  ``I'm going to call Coil for a vehicle, and to ask him a few questions, hear for myself that he talked to Kaiser.  However long it takes for the ride to get here, it should give me time to stitch Skitter up.''



I winced.



``Patch her up?  Why?''



``Not relevant to the current situation.  We'll explain later,'' he said.



``Later then.  Take care of yourself, Skitter''  Lisa hung up.



Brian held up the needle and thread, ``Let me apologize in advance.''



\blacksquare



``You see kids get their ears twisted in the movies and on TV all the time.  What you don't get is how much it fucking hurts,'' I touched the part of my mask that covered my bandaged earlobe.  It was throbbing, due in part to Brian's ministrations.



``Just leave it alone.  The painkillers will kick in soon.''



``Alright.''



We sat in silence for a few moments.  I stared out the small window at the back of the vehicle.  Very few cars were going in the direction we were.



The interior of the vehicle that Coil had procured for us was filled with medical equipment.  There was a gurney, which I sat on, a second smaller type of gurney that could be disassembled and reassembled as required, up near the ceiling.  The interior was efficiently packed with medical supplies: an oxygen tank underneath the bench where Grue sat, a heartbeat monitor, lifejackets, tubes of all shapes and sizes, lockers and drawers with pills, splints and bandages.



It was, to all appearances, a real ambulance.  I couldn't say whether it had originally been an ambulance, and Coil had added extra compartments for weapons and for my bugs, or if he'd gone the other way and built the vehicle from scratch, to accommodate his additions.



We slowed down, and Grue leaned towards the front of the ambulance,  ``What's the holdup?''



``Blockade coming up,'' the driver spoke.  He and the woman in the passenger seat were Coil's people, decked out in paramedic's uniforms.  ``No sweat.''



He flipped a switch, and the siren blared.  Seconds later, he was revving up and moving without difficulty.  I looked through the rear window, and saw a line of police cars and PRT vans behind us, moving to close the gap they'd just opened in their formation.



``Hey, are we okay?'' Grue asked me.  He was outfitted in costume, helmet on and visor down.



``Hm?''



``I get the feeling you're angry.''



``If I'm angry at anyone for that thing outside the mall, it's myself.  Can we just drop that topic forever and forget it ever happened?''



``No, no.  I mean, are you angry that I didn't jump out of my seat to go fight Empire Eighty Eight, before we knew everything that was at stake?''



``Oh,'' I flushed, and my ear throbbed in response to the rush of blood.  Could've kicked myself.  ``I honestly don't know.  I wasn't expecting it.  I see the lengths you go through to take care of your\ldots family member, I think of you as a pretty honorable guy, you know?''  This was veering closer to the conversation-that-was-not-to-be-spoken-of than I'd like.  I deliberately left that thought hanging.



Grue rubbed the back of his neck, ``I'm not sure I'm as good a person as you're making me out-''



An impact rocked the ambulance, tossing Grue out of his seat and nearly knocking me heels over head.  The ambulance veered out of the driver's control, tipped, and landed on its side, bringing Grue against the underside of the stretcher I'd been sitting on.  The spare gurney and the contents of drawers and lockers around the interior spilled free and scattered around us.



``Fuck!'' the driver swore.  ``Fuckshit!''



I pulled free of the tubes and the half of a gurney that had fallen around me, and crawled toward the front to look between the two front seats.



It didn't look so different from Bitch's dogs in general shape.  It was a little larger, too, maybe, but that was a hard call to make.  It was hollow, its limbs were thinner than the dogs, and I couldn't really draw a line between what was the actual `meat' of the body and what wasn't, because the entire thing was a chainsaw whir of serrated blades, hooks and needle points, shuffling and shifting around one another, rising and falling, all moving too fast for the eye to follow.  Altogether, it maintained a general quadruped shape with a tail and elongated snout.



Walking on either side of it were two people.  There was a pale, tall man with the sort of muscle-heavy build you only saw on cons and bodybuilders.  He wore black slacks that were in tatters around his feet, had chains wrapped around his forearms, hands and calves, and a blue-white tiger mask.  On the opposite side of the metal beast was a twenty-something girl with a gymnast's build and scars criss-crossing her exposed skin.  Her hair was shorn to a bleached blond buzz cut, and her face was covered by a metal cage.



The blender of dangerous looking metal bits dissolved, each of the hooks and blades retracting into the skin of the man at the center of the thing's chest.  As the front legs withdrew into his shoulders, he dropped into a crouch on the street.  He wore a wolf mask of sheet metal that had been crudely bent into place, framed by long, greasy blond hair.  Hookwolf.



Rumor had it that Hookwolf, back in the day, had been one of the top fighters in a parahuman fighting ring in New York.  He'd grown greedy, killed the man that ran it for access to the vault with the night's earnings, and had made a good number of enemies in the process.  It had been a group of white supremacists local to that area that had given him shelter and support, happy to side with him because the man he'd killed had been an `acceptable target'.  Maybe the ideology was real for Hookwolf from day one, maybe it was an act that had become reality when he found he enjoyed having people celebrate him for enacting his most twisted impulses and racking up a body count.  Either way, I suspected that  there were few things he wouldn't do for his `Empire' nowadays.



Stormtiger, the man with the chains and tiger mask, and Cricket, the girl, apparently tied back to the same circles of parahuman prize fighters that Hookwolf had once been part of.  I couldn't begin to guess their motivations for following him, but I suppose it hardly mattered.  Hookwolf was dangerous enough on his own.  With friends?



``We run,'' I muttered.  Hookwolf and his buddies had their backs turned to us and were walking toward the police barricade.  Stormtiger flexed his hands, and the air blurred around them, congealed into a half-dozen pale, translucent blades that jutted from each hand.



``We have guns,'' spoke the driver, ``We shoot them from behind.''



``No,'' Brian spoke, ``It won't hurt Hookwolf, and I suspect Cricket and Stormtiger could do something about it, or they wouldn't be so brazen about walking towards those cops.  Skitter is right.  We retreat.  Ready?''



Grue blanketed the back doors of the ambulance in darkness to mute the noise as he cracked it open to cover the outside as well.  Noiselessly, the four of us backed out of the ambulance.



Grue flooded the block with darkness, and I scattered my bugs out from the surrounding area and the compartments in the ambulance's interior to follow in the wake of the darkness, spacing them out to cover the ground and the other objects around us, giving myself a swarm-sense of my surroundings.  I grabbed the hand of the woman `paramedic' and pulled her away from the middle of the street, toward the sidewalk.  Brian brought the driver in the same general direction.



My bugs felt someone come after us, fast.  I didn't have time to get out of the way \emph{and} lead Coil's faux paramedic to safety as well, so I shoved her in one direction and leaped in the other.  The man leapt into the space we'd vacated, and I felt a rush of wind set my hair to whipping around my face.



There was an explosion of sorts, a blast of wind powerful enough to lift me off the ground and push away a fair share of Grue's darkness.  Stormtiger stood in the epicenter of the clearing, reforming the translucent `claws' around his raised left hand.



He used one of the translucent blades on his hand to tap the side of his tiger mask's nose as he turned to look down at me.  When he spoke, his voice was deeper than Brian's, ``Don't need to see you, sweetie.''



I was really, \emph{really} growing to hate enhanced senses.





