





Stormtiger raised one hand in the direction he'd come and created a blast of wind to clear a path through Grue's darkness and reveal Hookwolf and Cricket.



``Fancy this,'' Hookwolf chuckled, looking down at me, ``We decide to attack the blockades and avoid being hemmed in like the ABB was, and we happen upon you?''



``Not looking for a fight,'' I told him.



``Stormtiger, find the others of her group.'' Hookwolf snarled, apparently not considering my words worth responding to.



``Can't,'' Stormtiger spoke, from where he stood above me.  ``Not smelling them.''



``You smelled \emph{her}.''



``And I smelled the two uniforms from the ambulance.  Other one's bleeding, sitting near the ambulance somewhere over there.  Darkness boy isn't around anymore or I'd be able to smell him.''



He was \emph{wrong}.  My bugs could feel Grue out there.  If the driver had been injured, that might account for why Grue had lagged behind.  But Stormtiger couldn't smell Grue?



Hookwolf turned to me, ``The dog girl.  Where's Bitch?''



``Not here.''



``I know that,'' he growled.  His hand dissolved into a mess of knives, hooks and spearpoints, then solidified into an oversized claw with fingers as long as his torso.  He flexed them experimentally.  How did you even classify that?  Ferrokinetic shapeshifting?



I crawled backward a few feet, trying to maintain distance between us.  Stormtiger reached down and blocked my retreat with one blade-covered hand.



I looked up at Stormtiger and spoke, ``We split up earlier today.  One of our members had a source, we heard about the email that went out when the news stations and papers did.  Decided it'd be better to back off, just in case.''  No harm done by admitting that much.



``Don't believe you,'' he snarled.  ``Doesn't explain why you're here.''



``That's because-''



I stopped as the two of them turned away.  The `paramedic' a few feet from Stormtiger had bolted, and was drawing a gun as she ran toward the closest patch of darkness.  As she got close to her destination, still running, she turned on the spot and raised her gun to fire at Stormtiger and Hookwolf.



Hookwolf barely reacted as the bullets punched into his chest, and even that was just the inevitable force of being shot.  Stormtiger raised one arm as if to protect himself, but the bullets were already veering off before they could hit him, leaving a trio of hazy trails in the air where they had turned.



``Handle her, Cricket,'' Hookwolf spoke, pressing a hand against his collarbone where a bullet had struck him.  The scarred girl with the buzz cut dashed forward, reaching behind her back to draw two scythe-like weapons, each only about as long as her forearm.



Coil's soldier turned to fire at the incoming villainess, but Cricket ducked to the right, then evaded left, in time with the noise of the gunfire.  The distance between them closed rapidly.  I didn't see what happened next, as Coil's soldier disappeared into the darkness and Cricket followed her in.



Hookwolf turned back to me, ``Suspiciously competent for an ambulance driver.  Pretty fucking sure that's one of Coil's people.  What are you doing with her?''



I didn't answer.



My bugs reacted to a funny noise from the direction of Cricket and Coil's woman, but I couldn't hear it myself.  Grue's power did strange things to sound.  I had more immediate concerns.



Hookwolf dropped his hand to his side, and I saw how the bullet had penetrated skin, but had failed to get any further than the interlocking grid of metal that sat in place of Hookwolf's muscle.  He smiled.  ``I was hoping you wouldn't answer.  It means we get to \emph{interrogate} you.''



\emph{Options, options, what were my options?}  Bugs?  They were around, but I got the impression that Hookwolf wasn't going to suffer that much if I swarmed him, and Stormtiger had some kind of aerokinesis, which was bound to be pretty effective against the lightweight bugs.  Knife, baton?  Not much better.   These guys were capable in hand to hand.  I wasn't.



Where was Grue?  I felt out with my power, and found him at the back of the ambulance with the driver.  Whatever he was doing, I hoped he would do it soon.  I needed his help.



I looked for Cricket, and found her in the blackness, dragging Coil's soldier back toward us.  I saw her emerge from the darkness, one of the miniature scythes buried in the woman's upper arm, the other buried in her thigh.  With a full-body effort, Cricket swung the woman forward and pulled the scythes free.  Coil's soldier rolled onto the ground before Cricket.  If her powers didn't give her an edge in fitness, she was pretty damn fit for her frame.



Was Coil's woman dead?  No.  The woman was breathing.  She was making lots of short, fast breaths, not moving, but she was breathing.



Hookwolf watched for a second before turning back to me.  ``Maybe I'll give Stormtiger some practice at getting answers out of people.  Those claws of his?  They're compressed air.  Every second, he's drawing in more air, shoving it into that claw shaped space, to make them denser, harder.  And when he releases it\ldots'' he offered me a low chuckle.



\emph{Come on, Grue}.  I couldn't handle this alone.



``Want to see what happens when one of them is buried inside you when he turns it into one of his blasts of wind?''  Hookwolf asked.  Again, the low laughter at my expense.



Grue was moving toward me with purpose, now.  I stirred bugs from the ground around him to place them on his body, get a sense of what he was doing.  He was carrying something three and a half feet long, nearly a foot wide, a rounded off shape that was all smooth metal.



\emph{Shit}.



I flipped over and scrambled away.  Stormtiger was behind me, and he kicked me in the back as I tried to rise up and start running, shoving me back to the ground, hard.  I was glad for my mask as my face bounced off the pavement.



\emph{Go with it}.  Remembering the tips Brian had given me during our sparring session, I used the fact that Stormtiger had created a bit more distance between us and continued to move away as fast as I could manage.



``Running?'' Hookwolf laughed, ``You can try.''



``Gun oil,'' Stormtiger called out, whipping around to face Grue.  ``I smell gun oil.''



Grue hefted the long metal object back with both hands, then flung it forward.  He didn't drop both his arms as he let go.  Instead, he used his left hand to follow up with a directed blast of darkness to cover it as it rolled into the clearing.



I clamped my hands to my ears, painful as it was with the bandage on my right ear.



Grue's right hand was already withdrawing a gun from his jacket pocket as he backed up.



His arm jerked twice as he fired the gun at the oxygen tank he'd fetched from the back of the ambulance.  The first shot missed.  The second didn't.



It was so quiet I thought I'd been deafened by the sudden explosion.  Hookwolf's delayed scream of pain and rage was a bittersweet relief.



Wasting no opportunity, Grue marched forward, gun in hand.  Stormtiger had been farther away, and lay face down on the ground, bleeding badly but intact, from what I and my bugs could see.  Grue stopped, aimed, and shot him once in each leg.



``Hey!'' Cricket's voice was strangled, strained.  I wondered if one of the injuries that had given her one of those scars had done something to her vocal chords.  She lowered one of the scythes toward Coil's soldier.  ``I got a-''



Grue covered her and her hostage in darkness and turned toward me and Hookwolf.  The message was clear.  He wasn't negotiating.  I was pretty sure I couldn't have made that call, even knowing that stopping for the woman's sake was almost inevitably going to lead to a worse situation.



Hookwolf staggered to his feet.  He'd taken more damage from the blast than anyone, and his skin hung off in tatters around the arm he hadn't yet transformed, most of the trunk of his body and his thigh, with lesser damage over the surrounding area.  Beneath the tatters of skin, as I'd seen with the bullet wound, there was only blood-slick bands and blades of metal.  Hooks and knives all laid side by side in the general shape of human musculature.



Hookwolf thrust his damaged arm out to one side, and the muscles unhinged like a swiss army knife, revealing still more blades and hooks that unfolded, swelled and overlapped to cover and patch the injured area.  His arm grew with the use of his power, and the resulting limb was three times the normal size, ending in what looked like a two foot long fishhook.



``Skitter,'' Grue called, ``Run!''



I climbed to my feet and hurried toward him.  Hookwolf turned to face me, then lunged my way, closing more distance than I might have anticipated.   I abandoned my attempt to rejoin Grue and headed to my left, straight into the darkness.



My bugs dotted the surface of a mailbox, three paces into the blackness.  I ducked around it as Hookwolf blindly followed me in.  Swinging blindly, he struck a fire hydrant, but no water was forthcoming.  He lunged left, gouging chunks of brick from a wall, then he leaped right, striking the mailbox and cleaving it in half.



I was already scrambling in Grue's general direction, the mailbox well behind me.



I felt a surge of relief at realizing that Cricket had abandoned her hostage in favor of going after Grue, to initiate a brief exchange of blows.  Unfortunately, my relief was short lived, because the combat wasn't brief in a good way.  Grue fired the gun twice, and twice she dodged the bullet, standing only ten and seven feet away from the barrel.  It wasn't superspeed, either, though she \emph{was} quick.  Her movements were simply too efficient, and if there was any delay in her reactions, I wasn't seeing it.



He swung a punch as she closed in.  Cricket leaned out of the way, then swung her scythe to rake him across the chest.  From the way he staggered, I knew she'd struck home.  He jabbed, she avoided it as though it were easy, then followed up with two more swings, and he failed to avoid either.  He staggered back, clutching one arm to his chest.



He blanketed the area around them in darkness, filling the clearing, and Cricket immediately switched to swinging blindly and ferociously around herself as she advanced toward where Grue had been.  Grue backed away, but this had the unfortunate effect of putting him closer to Hookwolf, who was doing much the same as Cricket.  Grue turned and ran to create some distance and avoid being hemmed in.



Then every bug in the area reacted to that sound I couldn't make out, the one I'd heard when Cricket went after Coil's soldier.  It was loud enough for them to hear through the darkness, but\ldots entirely out of my range of hearing.



I couldn't say for sure, but I got the impression the ones closer to Cricket had heard it a fraction of a second sooner.



``Grue!'' I screamed into the oppressive shadow.  ``Move!''



Cricket turned toward him and lunged in one motion, bringing both scythes down in an overhead swing.  Grue moved out of the way just in time.



``She has radar!'' I shouted, my voice barely audible to myself.  Didn't matter.  Grue could hear me.



Cricket passed one of the mini-scythes into one hand and then used her newly freed hand to wipe bugs from her skin.  They were gathering on her, and she was starting to feel it.  Good.



Again, that pulse emanated from her.  She maintained it this time, and my bugs began to suffer for it.  Their coordination suffered, they began to move slower, and their senses – such as they were in the darkness – began to go haywire.



After a second or two, I thought maybe \emph{I} was starting to feel it too.  A bit off-balance, nauseous.  Grue was hunched over, his hands on his knees, but I wasn't sure if that was Cricket's power or the injuries she'd inflicted.  From the way Cricket was moving, I gathered that she couldn't see us.  Was it echolocation?  Did it not work if she simply blasted the noise continually rather than use it in bursts?



Annoying as it was that \emph{everyone} seemed to have a way of dealing with my bugs, I was at least putting her in a position where she couldn't both find us and deal with them.



I was having trouble getting a sense of her powers.  I'd heard of her, seen pictures, read up on her on the wiki and message boards.  She was rarely more than a footnote, typically a suspect in a murder or arson case alongside Stormtiger and Hookwolf.  Never had I come across something like `Cricket has limited precognition' or `Cricket is a sound manipulator'.



The bugs started to fall away from her, losing their grip or ability to navigate through the air.  Knowing our advantage would soon disappear, I advanced towards her, drawing my knife.  I checked on Hookwolf, and found him scaling a building a distance behind me.  Was he trying to rise above the cloud of darkness to spot us or get his bearings?



I was three paces from Cricket when I felt the sound die off, then resume again for one brief second.  Another radar pulse.



``Careful!'' I shouted, adjusting my momentum and hurrying to back away.  Too slow.  She was already pivoting to swing at me.  The handle of one scythe struck me in the side of my throat, the actual blade hooking around behind my neck to halt my retreat.  Before I could do anything, she pulled me toward her.  I stumbled forward, and she adjusted her grip to swing the other scythe up and into the side of my stomach.



I doubled over and crumpled to the ground.



Grue shouted something, but his words didn't reach me through the darkness.



Cricket emitted another radar pulse, then lunged for Grue.  She caught him in the arm, this time.  Then she backed off, going for the continuous, sense-warping noise to put my bugs on the fritz once more.



Grue raised his borrowed gun and his arm bucked with the kick.  Cricket was oblivious as the gun fired off several times in a row, but whatever she was doing with her power was screwing with Grue's ability to aim.  None of the bullets struck home.  He stopped.  Either he was out of bullets, though it seemed too soon for that, or he wanted to conserve ammunition.



I climbed to my feet, feeling my side protesting in agony.  The blade hadn't penetrated my costume, but the sides of my stomach weren't armored and the cloth had done little to soften the jab of it, even if it had prevented me from being cut or disemboweled.  Cricket was bigger than me, stronger, and she knew how to use her weapons.  It had hurt.



When I was sure I could move without falling over, I lunged, knife in hand.



I'd hoped that if I was quick about it, I could act before she used her radar again.  I wasn't so lucky.  She was already moving by the time I realized she'd made another pulse of noise, scythe points whipping around toward the side of my head, where my mask provided only partial coverage.  I had too much forward momentum to avoid walking straight into the incoming blades.



I half-fell, half ducked, and instead of driving my knife into her back like I'd intended, I wound up burying it in the side of her thigh.  Whatever technique let her dodge bullets, it apparently didn't work if she couldn't see.



As much as it might have hurt, she didn't waste an instant in hefting her weapon to retaliate and swinging down at my head.  I wasn't in a position to get out of the way.



Grue caught her by the wrist mid-swing and pulled her off-balance before she could follow through.



She moved fluidly, considering the blade buried in her upper leg.  She reversed her grip on her weapon with her free hand, stuttered her power to create what I took was another radar pulse, then readied to swing it at Grue.



I twisted the knife, and pulled it out of her leg with a two-handed grip.  Or, to rephrase, I pulled the knife \emph{through} her leg, dragging it horizontally through the meat of her thigh, toward her hip, and out.



She toppled, and Grue put his hand on my shoulder to pull me back away.  Cricket lay on the pavement, pressing her hands to her injury.



``You okay?'' Grue asked me, as he cleared the darkness within one foot of the both of us.



``I'm bruised but yeah.  I should be asking you that question.  How bad is it?''



He banished the darkness around his body, and in the gloom, I saw how the blades had neatly cut through his jacket and t-shirt to draw criss-crossing lines of red across his chest.  An uglier wound marked his right arm from elbow to wrist, all the more visible because the cut had extended to the cuff of his costume, leaving the sleeve to hang loose around his elbow.



``Looks worse than it is.  I've fought people like her before, in sparring and fighting classes.  She was showing off with the first few cuts.  Shallow, inflicting pain, not really meant to disable or deal real harm.''



``That's stupid,'' I muttered.  ``I'm glad, but it's stupid.''



``She probably didn't think about it.  I'd bet it's something she learned and incorporated into her style while fighting for a crowd.''  He looked over in Hookwolf's direction, then winced at how the movement pulled against his injured chest.  ``We should go.''



``Agreed.''



Grue opened a path in the darkness for the faux paramedic, we checked that she was alive, and then helped her limp to the ambulance, with me doing most of the heavy work for once.  I hurried to grab some first aid supplies, packing ointments, pills and bandages into a bag.  Coil's soldiers retreated back toward the police barricade before I was finished, each supporting the other.



Grue flooded more of the area with darkness while I gathered most of the swarm back around myself.  I left only the bare minimum of bugs necessary to navigate the sightless world of Grue's power and the ones I needed to track Hookwolf's presence.  There were more I couldn't touch because they were caught helpless in the endless, subsonic drone that Cricket still emanated, but I had enough that I could deal.  We hurried away before Hookwolf thought to attack the spot where the ambulance had crashed.



We were nearly four blocks away before Grue felt it safe to dismiss the darkness around us.  Rationally, I knew we were safer in the shadows, that it would prevent most ambushes, but a primal part of my psyche was glad to be in the light and noise once more.



I shot Grue another worried look as we walked.  ``Looks like it's my turn to give you some stitches.  You going to be okay?''



``Fuck.''  He touched his chest tenderly, not giving me a direct answer.  ``What were her powers?  Overclocked reflexes and what was it you said?  Radar?''



``Enhanced reflexes is a better guess than what I'd come up with.  She was making some sort of subsonic drone.  It was the source of that disorientation effect.  She could use it like echolocation or something.''



``It's times like this I can say it's worth having Tattletale on the team.  I hate not knowing someone's powers.''



We stopped at an old church with boards up where there should have been stained glass windows.  Litter and more than one half-full trash bag occupied the ground at the base of the building.  Together, we walked inside.



Regent was perched on the lip of the stage beneath the altar.  Tattletale sat on the back of one of the benches, her feet resting on the seat.  Bitch paced at the rear of the church, the point farthest from the front door, and her dogs moved like gargantuan silhouettes in the darkness of the aisles.  If it weren't for the light filtering in between the plywood on the windows, I wasn't sure I would have known they were there.



``Grue!'' Tattletale leapt from her seat.  ``What happened?''



``Ran across Hookwolf, Stormtiger and Cricket.  Those three like to cut people,'' Grue spoke.  ``We were lucky to get away as intact as we did.''



``Sit,'' I ordered Grue.  Hissing between his teeth, he pulled off his jacket, then turned his attention to his T-shirt, which was sticking to his chest with the blood that had leaked from the cuts.  Rather than have to remove his helmet and drag the cloth over his injured chest and arm, he tore his shirt where it had been cut, and pulled it off in tatters.  He sat down, shirtless, his helmet on.  I began getting the stuff out to clean his wounds



``Did \emph{you} guys run into trouble?'' Grue asked.



``Just enough that we've been getting a little restless. Bitch took down some thugs, but they scattered, and word's probably out that we're in the area.''



``Purity?'' He asked.



``She's out there,'' Regent spoke, in his characteristic distracted, disaffected manner, ``We saw the lights and heard the noise as she was knocking down more buildings.  She moved away from this area a little while ago.''



Tattletale turned to me, ``Here, give me that.  I'll work on his arm.''



I duly handed over the cleaning solution and some antiseptic wipes.  I heard Grue mutter, ``Shit, I hope Cricket isn't the type to put poison on her weapon.''



``Don't say that!'' I gasped, horrified.



``Not to worry, either of you,'' Tattletale sounded exasperated.  ``My power says no.''



I nodded, but my heartbeat was still cranked up a notch from that momentary alarm.  When I glanced up from the stash of medical stuff I'd grabbed from the ambulance to see how Tattletale was doing with Grue's arm, I saw Grue's skull-visor pointed at me.  Was he looking at me?  What was he thinking?  What expression was on his face?



``I'm thinking guerrilla strikes,'' Grue spoke, turning to Tattletale, ``We have the dogs, we use their mobility to harass, catch any roaming groups off guard, take them down, disappear before reinforcements or heroes show.''



Tattletale shook her head, ``One problem with that.''



``Which is?''



She pointed at his chest.  ``You may not be poisoned, but you've lost some blood.  I'd lay even money that you'd pass out if you did something as high exertion as riding the dogs.''



``Don't take a bet with Tattle,'' Regent chimed in, ``She cheats.''



``We need to end this fast,'' Tattletale said.  ``Not just because of Grue's injuries, but because Purity's going to wipe out our neighborhood soon if someone doesn't stop her.  We take the most direct action we can.''



``Direct action,'' I echoed her.  I didn't like the sound of that.



``We go straight for Purity.''



``Fuck that,'' Grue shook his head, ``There's no way.''



``Way,'' Tattletale retorted.  ``It's not pretty, it's risky, but it's our best bet at ending this, one way or another.  Thing is, we've got to move fast or our opportunity will disappear.  Skitter, we'd better get started on the stitches, I'll explain while we do it.''



I swallowed, nodded, turned my attention back to the bag of medical stuff, and found the needle and thread.



``Like you said before,'' I told Grue, quiet, pulling the pre-threaded needle free of the spool, ``Let me apologize in advance.''



``Damn it,'' he muttered.





