





``You going to be okay?'' I asked, as Grue zipped up his jacket.  With his t-shirt removed, he was wearing the leather jacket over his bare, freshly stitched skin.  I couldn't imagine it was remotely comfortable.



``I'll be fine.  Let's end this ASAP.  Bitch?  The dogs.''



I winced.  I wasn't looking forward to riding.  It was too soon after our previous escapade, and I was still sore.



Bitch whistled and pointed, and we headed out the front door of the church.  The moment we were outside, Grue hauled himself up onto Judas' back, and I could see him hunch over for a moment in pain.



``Seriously, are you going to be-''



``I'm fine, Skitter,'' Grue spoke.  He was creating darkness around himself, and his voice had that hollow quality to it.  ``Just drop it.''



The `drop it' line hit a little too close to home, echoing what I'd said at the mall after Brian's rejection, and once or twice after that.  I was made acutely aware of that little rift I'd generated in what had been a fairly easygoing friendship.



Regent and Bitch were climbing onto Brutus, while Tattletale was examining her phone.  That left two dogs to ride.



I looked at where Grue sat, and decided it would be less awkward if I didn't ride with him.  I approached Angelica, extended my hand for her to sniff, then climbed onto her back.



``Tattletale,'' Grue spoke.  ``I thought we were in a hurry.''



She put the phone away, then climbed up behind Grue.



``Coil?'' I guessed.



``Yep.''



``And he's saying?''



``To be careful.''



Grue gave a hand signal, Bitch whistled to give the dogs the order, and we rode.



Angelica was happy to follow the others, which freed me from the burden of getting her to follow my instructions.  That only left me the task of holding on and ignoring the ache in my leg muscles and stomach.



Tattletale was able to give us a general idea of which direction Purity was, using her power, and it only took us a few minutes to spot the telltale pillar of white in the distance.  Purity's light, not aiming at a building, but lashing out.



As we got closer, the situation became clearer.  Purity, a flare of white against the backdrop of the gray sky, was surrounded by other figures, easy enough to make out with their predominantly white costumes.  New Wave.



The leader of New Wave had named herself Lady Photon, but in the wake of New Wave's founding, and the revealing of their secret identities, the media had latched on to the idea of a superheroine mom and dubbed her Photon Mom.  It was apparent to anyone who followed cape news that the name really bugged her.



Lady Photon's daughter and niece were in the air with her.  Laserdream and Glory Girl.  Mother and daughter shared the same general powers; flight, the ability to raise forcefield bubbles around themselves, and the ability to project lasers from their hands.  As a consequence, their fight with Purity was something of a light show.



Below, it seemed, there was an all-out war.



As she targeted Glory Girl, one of Purity's blasts of light slammed into the edge of a rooftop.  Debris showered down, but was deflected by a bright blue forcefield.  That would be Shielder's power at work.  He fought alongside Flashbang and Brandish, and I could identify Krieg, Victor, Othala and Alabaster in their immediate vicinity.  Further away were Night, Fog, Panacea, Vista and Clockblocker.



``Around!'' Tattletale pointed over Grue's shoulder.



Wordlessly, Grue steered Judas into a turn.  Bitch, astride Brutus, a bit ahead of Judas, looked over her shoulder and turned to join them.  Angelica was happy to follow after.  Together, we detoured left to a side street running parallel to the ongoing battle.



``Why?'' I called out.



``Safer!'' Tattletale replied, without turning to face me.



A crash behind me made me duck.  Manpower, a powerful seven foot tall athletic figure decked out in white and yellow, had been thrown through a brick wall.  Maybe more than one.  He seemed unhurt, but he was a fairly durable guy.  Personal electromagnetic shielding, if I remembered right.  He was still struggling to his feet after we left him behind.



``What's our plan!?'' I shouted, raising my voice to be heard as one of Purity's blasts crashed down to the street to our right.



``Get her attention!'' Grue replied.  He pointed,  ``Up!''



Bitch whistled, and Brutus surged forward in our pack.  Brutus turned partway into an alley and leaped.  He latched his claws on one wall of the building, half turned, then leaped across to the neighboring building.  Zig-zagging upward, he ascended to the roof in a span of seconds.



\emph{Oh hell no}.



Judas followed, and Angelica was only a heartbeat behind.  If I'd thought our travel over the rooftops on our last escapade had been rough, this was sadistic.  Or masochistic.  It depended on where I assigned the blame.



We reached the rooftop just in time to nearly be squashed by a huge chunk of building that dropped from the sky like a meteor.  Angelica lurched under me as she leaped to one side.



New Wave's fliers and Purity weren't the only ones in the air.  Aegis was also up there on the side of the good guys, but Purity had backup from Crusader and Rune.



Crusader was flanked by a half dozen translucent replicas of himself, each armed with a ten foot long spear.  He could use his power to generate ethereal simulacrums of himself, a legion of ghosts, if you wanted to be dramatic.  I was more willing to peg them as some sort of semi-sentient forcefield molded in his shape or some telekinetic energy infused with fragments of his ego.  Whatever.  The important thing was that his images could carry him up into the air, letting him fly, and they could pass through walls, armor and other solid barriers to impale you with those spears of theirs.



Rune was the source of the debris that had struck us, which was rising back into the air as I watched.  A teenage girl in the service of Empire Eighty-Eight, Rune was a powerful telekinetic capable of lifting nearly a ton.  Several things weighing up to a ton, judging by what I saw.  She hovered in the air, crouched atop a piece of building as big as a garbage truck, with more similarly sized pieces of rubble orbiting her.  The drawback to her power was that she needed to touch things before she could move them with her mind, but that seemed fairly inconsequential right this moment.



The pair of villains were running interference for Purity, distracting and trapping the heroes to set them up so Purity could blast them out of the sky.  Purity was too high up for us to interfere with, which meant we had to find another way to get her attention.



Regent handled that for us, sweeping his arm to one side.  Rune slipped from her position on her floating piece of balcony.  Another gesture from Regent, and the girl was left hanging from the side.



``Don't kill her,'' I told him.



``Right,'' he looked up at the girl.  Seeing her struggle, he shouted, ``Better make sure you can land somewhere safe!  I'm dropping you in three seconds!''



The rock drifted in our general direction, and we backed the dogs up.  When Rune was over the rooftop, Regent swept his hand to one side and brought her down to a painful landing.



``Fuckers!'' the teenager in the cowl and robe screamed, ``I'll squash you!''



The big pieces of rubble in the sky above drifted our way.  One suddenly stopped levitating and dropped.



We were already kicking the dogs into motion, leaping to the neighboring rooftop, when the debris struck with a series of crashes that suggested the debris had punched through the roof and even the one or two floors below it.



Crusader was apparently too occupied covering for Rune's sudden absence to come after us.  That meant that all we had to worry about was keeping from being crushed by Sabrina the teenage nazi.



Note to self:  I apparently wasn't one of those capes that was \emph{good} at the repartee, banter or name calling.



One piece of debris soared over our heads, then plunged to stab downward through the roof in front of us.  The dogs were agile enough to leap out of the way.



In the heat of the moment, we didn't anticipate it rising again.



The debris thrust up through the edge of the building's roof, and the dogs had to skid to a halt to avoid treading on crumbling rooftop.  With the damage the building had sustained, our footing grew unstable.  The ground sloped, Angelica scrabbled for a grip, and then the section of roof beneath us began to slide down toward the street.



Brutus pulled clear easily enough, but the continued drifting of the piece of debris forced Bitch to direct him down toward the alley, off the rooftop.



The rest of us had a harder call to make.  We were sliding off a precipice, and it was a good ten story drop to the street.  The nearest and only available rooftop to leap to was the one we'd just left, which was in ruins.



Judas, I saw, managed to clutch the edge of the sliding raft of rooftop and get the leverage for a jump.  Brian, Tattletale and Judas reached the alley, where they could rebound off the walls until they reached relative safety.



I was about to urge Angelica to do the same, when that drifting debris of Rune's shifted position to block off the alleyway.  Another of Rune's pieces of building approached from her direction, promising to smash us if through some miracle, the section of roof Angelica and I were standing on didn't break free.



But we had another option.  If I could only convince Angelica.



``Go!'' I shouted at her, kicking my legs.  She pushed forward, and the movement only accelerated the decay of the fractured rooftop beneath her paws, prompting it to slide and tilt.



Angelica ran toward the building to our right.  To the right of the alley.  She clearly intended to leap to the building face, use her claws to dig into position there\ldots and there would be nowhere to go from there.  Even if she could hang there indefinitely, or scale the wall back to the street, Rune would scrape us off the wall with a levitated piece of rubble.



I grabbed a horn at the side of her head and hauled on it, pulling her left.  She resisted, hauled right, but I tugged again.



``Go!'' I shouted at her.



She lunged straight for the floating piece of debris.  Her claws latched on it, and for a moment, we hung there, Angelica in an undignified pose with her upper body hanging onto the thing, back legs dangling.



It drifted downward, slow at first, then faster, as though Rune couldn't support the weight of us \emph{and} the chunk of building.  Angelica scrabbled for a grip, pulled her body up and forward, and found the footing to leap.



We reached the alley, Angelica found footing on the wall, and then made her way safely to the ground.



As we landed heavily, I fell from Angelica's back.  My hands were stiff from the deathgrip I'd just maintained, and my legs were a wreck.



Still, hard to complain.



``You okay?'' Tattletale called out.



``Yeah.  You guys?''



``Not so hot,'' Grue replied.



He was leaning against a wall, with Tattletale at his side.  Darkness radiated from every part of his body but his chest, and I could see how  he'd unzipped his jacket to investigate the damage.  He was bleeding from the cuts on his chest.



``Fuck, I knew you weren't good to go!'' I struggled to my feet and rushed to his side.  ``You pull your stitches already?''



``Other things to worry about!'' Regent called out.  ``Incoming.''



I looked, and sure enough, Night and Fog were striding into the alleyway.  Night sported high heeled boots that clicked as she walked, and there was the gender difference, but the two were otherwise very similar.  Cloaks, cowls, no logos or other decoration.  Gray for him and black for her.



``Retreat,'' Tattletale spoke, ``Just don't turn your backs to them.''



Fog moved forward, his limbs and legs dissolving into a cloud as he advanced on us.  His pace was slow, only a little faster than we moved walking backward.



Bitch had to whistle twice to get a growling Angelica to retreat.  The dog seemed set on protecting her master, attacking this threat, and was slow to obey.



The fog reached her, and we heard a strangled yelp, an unnatural sound from the throat of an unnatural animal.  I saw Bitch start forward.



``No!'' I caught her shoulder.



I might have argued, told her why she couldn't or shouldn't attack, how useless it would be against a man that turned to a sentient gas.  I didn't get a chance.



While our attention was on Angelica, Night took the opportunity to blindside Brutus.  He was thrown bodily into our group with enough force to to bowl us and even Judas over.  Night just stood there, standing straight, heels together, one arm outstretched in front of her.  I hurried to my feet, my legs and knees aching, putting one hand on Brutus' shoulder to steady myself.  It was then that I saw the damage she'd done to him.



A dozen gouges criss-crossed his side, each wider than my handspan.  One of the gouges had even shattered some of the protective bone plating.  Brutus exhaled slowly, shuddering.



She'd done \emph{that}?



I sent my bugs at the woman, but the delay Night had created had bought time for Fog to get close.  His mist blocked the path to Night, reduced the woman to a faint silhouette, and where the cloud passed, my bugs were crushed alive in midair.  The mist swelled forward, and we backed up as best as we were able.



I checked our escape route.  It was blocked by none other than Night herself.  Had she teleported?  Cloned herself?  No, it wasn't cloning.  I couldn't see her silhouette anymore.



``What the fuck is this woman?'' I asked, ``Tattletale?''



``You know how the Manton effect could maybe be a psychological block that comes parceled with our powers?''



I nodded, once.



``Okay, well, imagine that this woman got powers that let her turn into something so \emph{wrong} that she's got some sort of mental block that keeps her from transforming if anyone can see.  Maybe because she's so ashamed of being seen like that.  When nobody's looking, though, she's a monster.  Lightning fast and all sharp.''



``That's\ldots''



``Not even remotely close to the truth,'' Tattletale confessed.  ``But it's the best I can offer you.  Don't take your eyes off her.''



``Right.''



I began massing my bugs.  I was going to need to catch Night off guard, debilitate her enough to take her down before she retreated to safety.  Swarm her, swat her down, then we'd figure out how to deal with Fog.



A bit optimistic, but it was a plan, anyways.



Night reached into her sleeve and retrieved a canister.  I recognized it immediately.



A flashbang grenade.



``Tattletale?''



``I see it,'' she murmured her response.  ``Grue, we're going to need you to cover this shit.''



I felt a ton of weight suddenly press heavily against my back.



``Grue!'' Tattletale shouted.



Grue had fallen against me, and he slid from that position to staggered to the ground at my side, landing with his hands and knees on the ground.



``Blood loss,'' Tattletale intoned.  ``Fuck, Grue, pay attention, you've-''



Night pulled the pin from the flashbang and threw it high into the air above us.





