





Whether I shut my eyes or suffered the effects of the flashbang grenade, the effect would be the same.  The moment we took our eyes off Night, she'd become what Tattletale had termed `all monster'.



I opted to have more control over my temporary blindness, clamping my hands over my ears, dropping into a crouch to shove my face against my knees, eyes wrenched shut.  I sent every bug in my immediate vicinity toward Night, in the hope of slowing her down even a fraction.



The flashbang went off while it was still over us.  The last time I'd been around one when it went off, I'd had a wall between me and the detonation.  I wasn't so lucky this time.  It wasn't just bright and loud.  The blast rattled through me, left me dizzied, unable to balance, almost incoherent.  It was scarily like the concussion I'd endured.



Night was already moving.  My bugs were my only sense that still worked, but they couldn't get a grip on the surface of her body.  She moved too fast, and her skin was smooth and oily, slick with some sort of lubricant.  The result was that I couldn't really make her out in the darkness.  I only got flashes, the vaguest sense of how she was put together.  I was reminded of the ink blots I'd seen during my brief stay in the mental ward.  Every fraction of a second, it was a different set of ink blots, a different shape, all edges and angles and sharp points, entirely up to interpretation.



She struck at Judas a half-dozen times in the span of a second, her limbs flashing out and striking hard enough that I could feel the vibrations in the air.  Judas staggered away from her, colliding with me and one of my teammates.  I felt Judas' crushing weight against my own body, the raw meat feel of his flesh and the stone hardness of his bones smothering me, before he shifted his weight and lurched back her way.



From the way Judas' movements followed Night's as she moved back, and the rigidity of his face and neck, I knew he'd managed to get a grip on her with his teeth.  He weathered the hits as she continued to thrash him.  He seemed to be getting the worse end of the exchange, but he'd taken away some of her leverage.



Blinking, I tried to focus on Night, but I saw double.  For several long, terrifying seconds, I was unable to bring what I was seeing into focus.



Judas was thrown against a wall, and went limp.  The furrows Night had carved into his face left more gouges than untouched flesh, his face a mess of shattered bone and hamburger meat.  With Judas' bulk out of the way, I could make out Night, backing away.  My bugs settled on her, and she pulled her cloak up to shield her face, still walking backward.



Snapping my head around to check, I saw our escape route barred by Fog's mist.  I could see Angelica's silhouette in the midst of the cloud.  Bitch and Tattletale were struggling to drag Grue back away from the advancing mist.  Grue, too weak to stand, was trying to use his darkness to wall Fog off.  Grue might have stopped Fog entirely, except he was so weak that his darkness was dissipating almost as fast as he produced it.  Fog slipped through the largest gaps and continued a slow but inexorable advance.



Night was still struggling to get away from the bugs as they navigated around the folds of her cloak and the coverage of her mask.



Drawing my baton, I started to advance on her.  Night was human like this, vulnerable.



She drew her hand from her sleeve.  Another canister with a pin in it.



``Regent!'' I shouted.



He snapped his hand out, and Night's arm bent in a palsied, twisted angle.  The grenade fell to the ground, and Night fell on top of it.



I thought that Regent had been the cause of her fall, until I saw her raise her head, her good hand holding the grenade, pin held in her teeth through the fabric of her mask.



She pulled the pin free, and black smoke began billowing from the upper end of the canister.



It was suicidal, perhaps one of the dumbest things I'd done yet: I charged her.  She was already standing, holding the canister out in front of her to ensure the plumes of colored smoke obscured her quickly.  I struck at her hand with my baton, knocking the smoke grenade to the ground.  I stooped for it, but she stepped forward, blocking it with her body, seizing my shoulders.



She wrestled me to one side of the alley, perhaps to try and push me away and buy time for the smoke to build up, maybe for another angle.  I wouldn't find out, because I brought my baton against the side of her face.  I got a sense from the feeling of the hit that she didn't wear any armor or protective wear beneath the cowl and mask.



Night staggered from the blow, and I drove my shoulder into her.  It wasn't as effective as I'd hoped, but I did get her far enough away from the canister that I could duck down and scoop it up in one hand.



I dashed away, past her, and she struck me from behind.  I knew from the magnitude of the impact that she wasn't in her human shape as she hit me, and for one paralyzing moment, I suspected I'd made a terminal error.



The blow was enough to knock me to the ground and make me roll a half-dozen times before I could stop myself.  I cast a glance over my shoulder as I stopped.  Night was there, and the residual smoke from the canister that surrounded her had apparently been sufficient to block my teammates' view.  Stupid of me to turn my back.  I was lucky that she hadn't had more than a second or two in her transformed state to act.



I scrambled to my feet, not taking my eyes off her, and rapidly backed up.  A piece of the armor on my back dangled from where she'd cleaved through it, swinging against my backside in time with my steps.  I held the smoke grenade low, to minimize how much it obscured my vision.  When I'd backed up enough that there was an alley to my right, I threw the smoke grenade away.



Night stopped following me, then swept her cloak up to shield against the bugs that still swarmed her.  I couldn't go as all-out as I normally might with my swarm, without risking that I'd obscure my own vision of her and give her another opportunity to transform.



Second try, then.  Baton in hand, I charged her.



She was thrashing beneath her cloak, six or so paces away.  The bugs were nipping and stinging flesh.  Good.  One or two more good hits with the baton, she'd be disabled.



Night bent low, and I thought maybe she was down for the count.



Then she swept her cloak off and threw it up into the air.  It opened wide and momentarily filled my field of vision.



I heard her footsteps, two normal ones, heels clicking rapidly as she ran, then the noise of claws scraping against hard ground.  She tackled me, keeping the fabric between us, and my baton slipped from my grasp as her weight slammed into the trunk of my body.  The cloth of her cloak caught on my right hand and face.  An angular arm with too many joints seized my right leg, another two latched onto my right arm and neck, respectively.  Her grip and proximity to me held the cloth in place, kept her obscured.  I was hefted high into the air with a speed that dizzied me.



She dropped me, making me grunt as I landed.  Above me, my bugs touched her very human body.  I struggled to pull the cloth free, but it caught.  After a few seconds of ineffectually trying to remove the cloak from myself and see what was happening, I was almost frantic.  I brought my own bugs down on top of myself to get a better sense of what was happening.



Hooks.  The black fabric of the cloak was woven with black-painted hooks at regular intervals.  She'd worn that layer facing the outside.



``You're boring people, you know,'' I heard Tattletale's voice, and felt a fractional relief.  I focused on pulling the hooks free.  Not that many were caught on the fabric, but there were some caught on the textured exterior of my armor, others on the straps that held my armor in place, a couple in my hair.



``I saw your info.  Mr. and Mrs. Schmidt.  First located in Hesse, Germany, moved to London, then Brockton Bay, Boston, then Brockton Bay again.  No kids.  Cat.   Nothing interesting about you, besides the obvious.  I'm thinking you even have your dinners on rotation.  Chicken and rice on Mondays, Steak and potatoes on Tuesdays?  Something like that?''



I pulled the cloak free and held it in my hands.  I saw Tattletale on the other end of the alley.  Fog had advanced quite a bit, but Regent and Bitch had apparently gotten Grue up on Brutus' back, and both Brutus and Judas were with them, Brutus moving painfully slowly, while Judas was apparently blind or nearly blind from the damage to his face.  They all stood not far behind Tattletale, masked by traces of the smoke from the smoke bomb.



Night stood closer to me than the others.  I could see how she had various pieces of equipment strapped to her hips, forearms, and back.  Grenades, canisters, knives, something that looked like spray paint.  She swatted at the bugs that were crawling around her face and eyes, but her attention was on Tattletale.  I could have stood, maybe, but I didn't want to draw her attention.



``So I was at a loss to figure out how to fuck with you.  You're two dimensional.  Until I remembered that you left the Empire when Purity did.  And when she came back?  So did you.''



Night cocked her head a little to one side, listening.  Again, she slapped at the bugs on one side of her face.  Her face didn't feel swollen, from what my swarm was conveying.  Her eyes were open, blinking closed when a bug touched her eyelash.  I suspected she healed back to perfect condition whenever she entered her other form, which would include cleansing herself of any toxins or allergens.



Night looked down at me.  Pale blue eyes.



``Hey!'' Tattletale spoke, ``Pay attention!''



Night drew a knife from a hip sheath.  She bent down over me.  I dropped her cloak and struggled to reach behind my back for my own knife, but she was faster.  The blade pressed against my throat.  My hand caught her wrist, stopping her from going any further.  I was pretty sure my costume could take a cut from a knife, but if she found the gap where my mask was separate from the body portion of my costume that extended around the lower part of my neck, she could slide the blade through with no difficulty.



``Damn you!'' Tattletale shouted.  I was only aware of Night's unwavering, unblinking gaze, the feel of her wrist in my grip.  Then the gunshots.



Night didn't even scream.  She dropped partway on top of me, falling onto her side, her weight on my legs.



The villainess lay there, silently writhing, hands behind her back.  Blood welled from holes in her lower back and the space where her buttock met her thigh.  I glanced at Tattletale, who had her gun raised, looking slightly surprised and disturbed by what she'd just had to do.



Any sense of relief I felt at Night being taken out of action was short lived.



Too bright to look at, Purity hurtled down from the sky to land just beside Night and me.  I saw her raise one hand toward Tattletale and the others, energy welling up.



The blast of light momentarily blinded me, and it struck me just \emph{why} Purity had Night and Fog working as part of her personal squad.  There were no happy coincidences there.  She must have calculated how their powers could collectively work together.  Her light and Fog's mist could blind their foes, with Night leveraging any opportunities gained.  Alabaster and Crusader?  Probably intended as the front line, to slow the enemy down, take out the problem targets and buy time for the core group to do what they needed.  Or to do what they were doing now, and occupy enemies elsewhere.



When I could see again, I tried to grasp what had changed and what had happened.  Dust filled much of the alley, Night stood beside Purity, unhurt, and my teammates were on the ground.  No blood.  Nobody dead or dying.  At least, nobody that hadn't been dead or dying when Purity arrived.  I was getting worried about Grue.  He didn't look nearly as lively as he had two minutes ago.



A channel had been carved out of the brick wall to Purity's right.  Motes of light still danced around it.  An intentional miss?  No.  It would have been Regent throwing off her aim.



``Purity!  Kayden!  Not looking for a fight!'' Tattletale called out.  She raised her hands, her gun dangling from one finger by the trigger guard.



Purity just raised her hand, and more light began glowing in her palm.



``Dale and Emerson!''  Tattletale added.



Purity didn't lower her hand, but she didn't shoot either.  ``What?''



``Aster.''  Tattletale stood up, ``She's at Dale and Emerson.  Outskirts of town.  The PRT has a safehouse there, for when a villain's after someone, or in case some member of the Protectorate or Wards gets outed, and their family needs a spot to stay.''



``How-''



``You worked alongside me when we were dealing with the ABB.  Your subordinates and allies have as well.  You know I have my sources.''



``Don't believe you.  You have no reason to tell me this, you told everyone-''



Tattletale interrupted, ``We didn't tell the media that stuff.  I'm even a little pissed about it.  Not just about us getting blamed, but that they didn't just attack you, but your families?  It's fucked up.  Entire reason we came here was to set the record straight and get you your kid back.''



``Kaiser said-''



``Kaiser thought he'd get more out of this debacle if he turned you against us, first, before directing you at the people or person who \emph{really} sent the email.''



Purity shook her head.



Tattletale added, ``It's up to you.  Who are you going to trust, when Aster is on the line?  Me, or Kaiser?''



\emph{That} was her argument?  I started to move to where I could attack Purity if it came down to it.  A spearpoint pressing down against my collarbone stopped me.  I looked up and saw Crusader behind me.



Purity dropped her hand to her side.  She told Tattletale, ``You're coming with me.''



``Didn't expect any less.  But you're letting my team go, and this destruction stops.''



``And how do I know you're not just sacrificing yourself for them?''



``Because whatever else you might be, Kayden, you somehow, in some warped perspective, see yourself as an upstanding person.  And if \emph{I }wasn't an honest person when it counted, I wouldn't trust you to hold to that.  Make sense?''



It didn't to me.  It was circular reasoning.  I wouldn't have listened if it were Tattletale trying to convince me  The question was whether it would get through to Purity.



Purity stared at Tattletale for a long time.  I was acutely aware of the spear at my chest, which Crusader could thrust through my costume and into me with a momentary use of his power.  How easily Purity or Fog could give Night the opportunity she needed to slaughter my teammates.



``You're aware of the consequences if you're wrong?''



``I'm not stupid,'' Tattletale spoke, ``You take out your anger on me, I wind up dead or maimed.''



Purity stepped forward and grabbed Tattletale's wrist.



``The others walk,'' Purity spoke to her subordinates, leaving no room for argument or discussion.  She wrapped one arm around Tattletale's ribs, and they were gone in a flash of light, a trail of firefly-like lights dancing in Purity's wake.



In that same momentary glare that had carried our teammate and Purity away, Night had moved into the midst of our team.  She had a knife held with the blade pointed out of the bottom of her fist, pressed to Regent's throat.



``I get it,'' Regent replied, with a disinterested tone, ``You could kill us right here.  May we go?''



Night sheathed the knife and walked through the group to Fog, who was gathering himself up in a human shape again, turning away to exit the alley.  Crusader, on the opposite side of us, was rising back up to the sky.



I breathed a sigh of relief as Purity's squad disappeared.  I held my breath again when I saw Grue and, further down the alleyway, Angelica.  Grue's darkness was reduced to mere wisps around his body, which I took to be a bad sign.  Hurrying toward him, I retrieved my cell phone, went down to the bottom of the contact list.



It rang three times before it picked up.  I heard ambient noise, maybe a fan, but the person on the other end didn't respond.



``Coil,'' I spoke, ``It's Skitter.  We need that doctor of yours.  Fast.''



``Can you get to the same location as last time?''



``I don't know.  Grue and the dogs are hurt.  We may need a ride.''



``I will arrange it.  Expect a call from the driver shortly.''  He hung up.  Not quite so friendly as the last time we'd talked.



I set to helping Alec steady Angelica while Bitch worked with Judas, who'd been effectively blinded in the fight with Night.   She guided his head and shoulders under Angelica's body, so the smaller `dog' was draped over him.



Once Angelica was in position, I hopped up behind Grue and helped him turn him over, to examine his chest.  I applied pressure and used the remainder of the bandage I had in my utility compartment to try to staunch the bleeding.  When I talked to him, asked him to verify that he was okay, his replies were monosyllabic and fairly nonsensical.



Between Judas's canine burden and the damage Brutus had apparently sustained to his side, the two dogs moved slower than I normally walked as they plodded down the alley.



Every moment was nerve wracking.  I kept waiting for someone in the Wards, New Wave or Empire Eighty-Eight to find their way into the alley, spot us and pick a fight.  Worse, I harbored grave concerns that Grue might stop breathing.



The phone call from Coil's people came when we'd reached the beach – the closest spot I could think of that would put us out of line of sight in the continued fighting.  I directed the guy on the phone to our position, and in my nervousness, I had to get them to verify, twice, that they'd safely made it through the barricade without any trouble.  All we needed was another ambush at the barricades from more of Hookwolf's underlings.



The moment the pair of ambulances arrived, we loaded Grue into the back of one, the three dogs into the other.  Brutus and Judas had shrunk, having shed the layers of added bulk, and were more or less alright underneath it all.  Angelica, though, had been in Fog's mist, and wasn't any better even though she was almost normal size.  She'd inhaled the mist, drawn it into her lungs.  I could only surmise that it had consequently made its way into her bloodstream, and from there, to the rest of her body.  Only time would tell how much damage Fog had done to her from within.



I went in the ambulance with Grue, and watched as they gave him extra blood and tended to his chest.  Between my first time job patching up his chest, the fact that he'd torn it open, and my haphazard attempts to wad it with bandages and stall the blood loss as we retreated from the scene, it was a mess.  I cringed, feeling guilty, waiting for one of Coil's medics to call me on something I'd done wrong.  They worked in silence, which was almost worse.



I sent Tattletale a text:



Frog A.  Got Coil's people to pick us up.  Brian is getting help.  Dogs are mostly ok.  Text me back.



We pulled in behind the doctor's office, and Tattletale still hadn't replied.  I was surprised that the ambulance with Bitch, Regent and the dogs hadn't come with us.



The doctor was a cranky old guy that Coil's medic referred to as Dr. Q.  He was a thin-lipped man, about my height, which made him fairly small.  His hair was either recently cut or he got it cut regularly, was slicked close to his scalp, and seemed too dark given how old his face and hands were.  He took over for the medics as they carted Grue in, and they left with a nod to me.  I nodded back, unsure of how else to respond.



I stood by Grue's bed with my arms folded and watched.  Dr. Q checked the work the medics had done in suturing up Brian's chest and muttered to himself that it was competent.  When he'd verified they hadn't screwed up, he took the time to clean Brian's chest and remove the remaining threads from the first job.



``The bug girl,'' he finally commented.



``Yeah.  I'm really sorry about bringing the bugs to your place, last time.  I see they're gone now.''



``They are,'' was his response.



I nodded.  I checked my phone again.  Still no response from Tattletale.



Minutes passed.



``Okay,'' he pulled off his latex gloves, ``Nothing more we can do for this lug.  You unhurt?''



I shrugged, ``More or less.  Got jabbed in the stomach, I have my aches and pains, hurt my ear earlier, but I already got it taken care of.''



``I'll verify that for myself.''



He checked my stomach, which required me to take off the top of my costume, and he prodded the bruise Cricket had left me with cold, dry fingers.  Then he had me remove my mask to examine my ear.  Apparently, he didn't deem Brian's job satisfactory, so I was sat down on a stool so he could clean it up.



He was partway through the job when my phone vibrated.  I read it and heaved a sigh of relief.



Tattletale:



Avocado c.  she got what she needed.  omw





