





The skeleton of a building loomed over us.  Girders and beams joined together in what would become one of Brockton Bay's high rises, twenty stories tall.  At the base of it was a sea of crushed stone, with innumerable bulldozers, piledrivers, loaders, mixers and graders standing still and dark.  The only light came from the buildings and streetlights on the surrounding streets.



Tattletale put key to lock and let us through the fence that surrounded the site.  She held the gate open as Grue, Regent, Bitch and I filed through, followed by Judas and Brutus.  The two dogs were nearly normal in size, nothing that would raise alarm if someone saw us at a distance.  When we were through, Tattletale shut the gate and reached through the gap to put the lock back in place and click it shut.



Gravel crushed underfoot as we made our way to the unfinished high rise.  Tattletale pointed to a hatch, surrounded by a rim of concrete.  The hatch itself had a yellow warning sign reading `Drainage', sporting images beneath of a man wearing a hazmat suit and a man wearing a gas mask.  She fiddled with the keyring to get the right key, undid the lock and raised the hatch.  Stairs led down into a darkness that looked and smelled very much like a storm drain.



As we descended, the smell got stronger.  We passed through a door with metal bars, and then traveled down a long hallway.  The room at the end of the hall was small, with one other door and a small surveillance camera in one corner.  The door we faced had no handle, forcing us to wait.  It took about twenty seconds before someone opened the door for us.  One of Coil's men.



The interior of the sub-basement had none of the smell of the previous chambers, and consisted of two tiers with walls of poured concrete.  The upper level we stood on was an arrangement of metal walkways that extended around the room's perimeter.  Crates and boxes filled the level below, and I could see fifteen or so of Coil's people down there, sitting on crates or leaning against them, talking among themselves.



Each soldier was outfitted in a matching uniform: shades of gray and some black, hard vests with raised collars to protect their necks.  Only a few wore their balaclavas, and I could see a variety of nationalities in a group that was mostly men.  All of the soldiers had assault rifles somewhere nearby, slung over shoulders with straps and leaning against walls or crates.  Polished steel attachments on the underside of each gun's barrel contrasted with the dark gunmetal tone of the rest of the equipment.



The man who had opened the door for us inclined his head in the direction we were to go.  We traversed the metal walkway, and passed more of Coil's soldiers.  I saw one squad of six below us was gearing up, pulling on masks and checking their guns.  Five seconds later, we passed Circus on the walkway, in a costume and makeup of red and gold.  Oblivious to us or our passing, she was leaning against a wall by a stack of cardboard boxes, standing intimately close to a young soldier with close-cropped red hair and an ugly scar running down one side of his neck.



We found Coil at the end of the walkway, talking to four people who most definitely weren't soldiers.  Each wore a suit, and none seemed the type to carry a gun.  There was a heavyset woman, a man who must've been fifty or sixty, a man who stood no more than four feet tall and a blonde woman who barely looked out of high school.



``Cranston, can you have it for tomorrow?''



``Yes, sir,'' the blonde woman replied.



``Good.  Pearse, the soldiers?''



``Squads Fish, Nora and Young are suited up and ready for your okay,'' the short man spoke.



``And the replacement recruits?''



Pearse handed Coil a set of folders, ``I've put post-its on the most promising.  We need two to make up for one soldier that was recently injured, and one that decided to skip town.''



Coil tucked the folders under one arm, ``Good.  Duchene, I'll talk to you later tonight about our preparations.  The rest of you, I'll see you tomorrow night.''



The suits marched off, with all but the fat lady passing us to go the way we'd come, along the metal walkway.  The woman headed down the stairs to the lower area with all the soldiers, and a group of people that weren't in uniform flocked to her.  People with clipboards and crowbars.  The construction crew?



``Undersiders,'' Coil spoke, ``You've recuperated this past week?''



``More or less,'' Grue replied.  He had his arms folded.



``Excellent.  And what do you think?''  He gestured to the underground complex around us with a sweep of his arm.



``It's impressive,'' Grue spoke.



``Once things are set up, some of this will be a base of operations for the Travelers, the rest of this space serving as a place my men can meet before they deploy.''



``Right,'' Grue replied.



``So.  I expected a reply once you felt you were healed and ready for more work, or if you decided on a reply for my deal, but I got a sense this isn't quite that.''



Tattletale spoke, ``We can't keep doing this, Coil.''



It was hard to tell, but I suspected that did something to knock Coil off his stride.  ``Hm.  Elaborate?''



``We keep getting through these fights by the skin of our teeth.  We're not up to it.  Just a few days after we helped take down the ABB, a situation that had two of our members facing down Lung and Oni Lee, we were up against the Protectorate, the Wards and Empire Eighty-Eight in the span of forty-eight hours.  Even with your people and your powers to help, we're not strong enough for this.''



``I see,'' Coil turned to face the lower section of the sub-basement and look down at his people.  He rested his hands on the railing, ``Are you terminating our arrangement?''



Tattletale shook her head, ``We'd rather not, but it depends on what we agree to here and now, in this meeting.  We talked this over for the past week, and I'll be blunt.  The one person who wasn't keen on taking your deal changed her mind, but the rest of us now have some serious reservations.  And it's not just the issue of our safety.''



Coil nodded.  ``Well, let me start by saying I'm pleased to hear about your change of heart, Bitch.  Can I ask what prompted it?''



Bitch shot Tattletale an irritated look, clearly unimpressed that Coil had been informed on our negotiations.  Still, she gave him a response.  ``Decided it wouldn't be so bad to get help with my dogs.  I still think you're full of shit, but way I see it, you can be as full of shit as you want, so long as I get what I want.''



``I suppose I'll take what I can get.''  Coil sighed a little, ``Which leads me to our subject of discussion.  Would I be right in assuming these reservations our Tattletale has mentioned have something to do with me, and how I operate?''



Grue and I both nodded.



``And you're among these individuals with doubts, Tattletale?''



``Sorry.  I've worked with you for a while now, I know what you can do, I even like and respect you.  What you're going for.  But this last play of yours was fucked up on a lot of levels.''



``Yes,'' Coil conceded, turning back towards us, ``You're right.  Too heavy handed a maneuver.  A tactical nuke where a rocket launcher might have sufficed, with undeserving parties suffering for being too close to the real targets.''



``Us, and the families of the members of Empire Eighty-Eight that you outed.''



Coil nodded, ``So the two main points we need to discuss are the apparent carelessness of my maneuver against Empire Eighty-Eight, and the risk your group has been facing in the field.  That said, if these issues are addressed in a satisfactory manner, would I be right in thinking you are prepared to accept my deal?''



Tattletale glanced at each of us, myself included, then told Coil, ``Maybe.''



``Good.  Shall we walk?  I'll be more able to answer your second concern when we get to the other side of this complex.'' He stepped away from the railing and extended a hand, inviting us to join him.  He walked with his hands clasped behind his back, leading us around the end of the room to the walkway opposite the one we'd traveled to reach him.



``First off, apologies are in order,'' Coil spoke, ``Your concern over the way I outed the Empire's members is entirely deserved.  In truth, it was a plan I had begun before I even knew of your existence, Undersiders.  My initial attempts to divine the secret identities of my enemies were slow to bear fruit, and my hired men often underwent weeks of investigation only to find they had been barking up the wrong tree.



``For almost four years, I have invested funds and time in the possibility that I could find the weak point of my enemies: their civilian lives, the faces under the masks.  For years, I was disappointed.  In my early days, I had less money to fritter away, my facility with my own power was not what it is today, and many of the failures on these fronts were costly.



``As I began to amass my fortunes, this became easier.  I could hire better investigators, pay the right people to divulge information and unseal court records.  Pieces began falling into place.  With my recruitment of Tattletale, I was able to avoid a number of wild goose chases.  It was still slow, and the turnover rate of Empire Eighty-Eight was frustrating, especially as I aimed to have the complete picture, with no member of Kaiser's empire left unmasked.  My efforts with the local heroes were no better, if for different reasons.



``For some time, aside from regular payments and some direction, my attention was elsewhere.  It was only two weeks ago that I was contacted by my investigators and told that I had what I wanted on Empire Eighty-Eight.  To have it come together at that time, when the Empire was one of the sole barriers remaining before me, it seemed to be serendipity.  I jumped on the opportunity.''



Grue spoke to Coil's back, ``And you forgot about us.  What it might look like.''



Coil turned his head, ``Yes.  I'll admit I am not proud of my failure to see the bigger picture, and I assure you, it is not a mistake I am prepared to make again.''



``That's it?  You say `I'm sorry' and we're just supposed to accept it?'' Regent spoke for the first time since we'd arrived.



Coil stopped, and we were forced to stop or we would have walked right into him.  He spoke, ``If you accept my deal, I will undertake no plan of this scale without first consulting you, the Travelers and the independent villains that work for me.  It is my hope that you would be able to inform me about any flaws or unintended consequences regarding my schemes.''



Grue unfolded his arms, ``I can't say for sure.  Maybe.''



I spoke, ``I like the idea, but no offense, I'm not sure I trust you that far.  And don't say that Tattletale would find out and tell us if you bent the rules and tried to slip something past us.  She's not infallible.  Sorry, Tattle.''



Tattletale shrugged at that.



``I'll leave you to think on the idea,'' Coil spoke, ``There's no action or gesture I can really take that will earn your trust in one fell swoop.  All I can do is to work with you, giving you no more reason to \emph{distrust} me.''



``Sure,'' I replied, noncommittal.



``Now, that leaves one us final issue to remedy.  Your worries for your safety.  I wish to show you that you are in good hands, and I'm prepared to reveal one of my secret weapons,''  Coil came to a stop outside a door.  A soldier stood nearby, smoking a cigarette.



``Fetch her,'' Coil ordered.  The soldier nodded, squashed the cigarette against the wall, pocketed the butt and went through the doorway.



Coil walked over to the wall where the soldier had extinguished the cigarette and used his thumb to wipe the smudge on the wall away.  He spoke to us, ``If I told you I knew where Kaiser was hiding out from the heroes, alongside his bodyguards and perhaps a handful of his lieutenants, that I wanted you to defeat them in a nighttime ambush, this would be an example of the sort of situation you're concerned about facing?''



``Yep,'' Tattletale replied, ``Even with your power--''



``--You have your worries, yes,'' Coil finished for her.  ``Forgive me if I do not elaborate on the subject of my abilities, or give Tattletale permission to do so.  We- ah, here she is.''



The soldier came through the door, with a girl in tow.  Twelve years old or so, she had dark circles under her eyes, and straight, dark brown hair that was in need of a trim.  She wore a white long sleeved shirt, white pajama bottoms and white slippers.  She didn't make eye contact with anyone, staring at the ground.  Her right hand gripped her left elbow, and the fingers of her left hand drummed an inconsistent beat against her thigh.



Coil bent down and pushed the hair away from the girl's face.  She looked at him, then looked away.



``I need some numbers,'' Coil spoke, gently.



``I want candy.''



``Alright.  Candy after six questions.''



``Three,'' she grew more agitated, turned as if to walk away, then turned back in his direction.  She was fidgeting more.



``Five questions.  Is that fair?''  Coil turned and sat on the metal walkway, beside where the girl stood.



``Okay.  Five.''



``I'd like these people,'' Coil pointed at us, ``To go fight Kaiser, tomorrow night at eleven in the evening.  You remember them?  The Undersiders.  And you remember Kaiser?  From the pictures I showed you?''



``Yes.  You asked me this before.''



``I did.  But I want the Undersiders to hear what you say.  Give me a number.  How would they do, without my help?''



``Forty-six point six two three five four percent chance they all come back.  Thirty three point seven seven nine zero one percent only some come back.  That's one question.''



Coil paused to let that sink in, then looked up at us, ``She calculates possibilities, we think she does it by seeing all the potential outcomes of an event in a fraction of a second.   Her power categorizes these outcomes and helps her to figure out the chance that a given event will come to pass.  It isn't easy for her, and I try not to tax her abilities, but you can surely see why this is so valuable.''



I hugged my arms close to my body.  When I glanced at the girl, I caught her looking at me.  I looked away.



``Candy, now?''  She started to bite at her thumbnail.  Looking at her other hand, I saw her nails were bitten to the quick.



He moved her hand away from her mouth, ``Four more questions, pet, then candy.  Tell me the numbers for the same situation, but if I sent the Travelers instead.''



``Sixty point two one zero zero nine percent chance they all come back.  Forty-four point one seven four three percent chance but someone gets hurt or killed.''



``Good girl,'' he turned to look at us, ``The Travelers are powerful, so it stands to reason their chances are higher.  But I've found that your group benefits more from a use of my power.  Pet, tell me the numbers for the same scenario, for both the Travelers and the Undersiders, but let's say I was helping them in my usual manner.''



``That's two questions.  Two teams, two questions.  No cheating.  I get really bad headaches when I try to get too many numbers.''



``Okay.  Answer those two, then there's one more before you get your candy.  I just need to know the chances that the teams will come back intact.''



The girl nodded, a little too quickly and eagerly, ``Those people there have a thirty-two point zero zero five eight three percent chance to come back with nobody dead or seriously hurt if you help them.  The Travelers have a forty-one point--''



``No, stop,'' Coil stopped her, ``That doesn't make any sense.  You gave me different numbers before.  Those numbers are \emph{lower} than the ones they'd have if I didn't help.''



``It's the numbers in my head.''



``The numbers are wrong, pet.''



She shook her head, raised her voice in a surprisingly sudden fit of anger, ``No!  They're right!  You just don't want to give me any candy!''



Coil put a hand on her shoulder.  She pulled away, but he held her firm.  He had to raise her voice to be heard over her squeals, and he shook her just a little to be sure she was listening, ``Last question, then you'll get your candy, I promise.''



She began to settle, and Coil was calmer when he spoke again, more like his usual, reasonable self, ``Just give me the number, again, if I sent the Undersiders out to fight Kaiser, without giving them my help.  What percentage, that they come back intact?''



``Twelve point three one three three percent--''



Coil stood, swiftly.  He turned to the soldier that stood nearby, ``Give her what she wants.''



The soldier guided the girl back through the door.



Coil muttered to himself, ``There's some anomaly at work, here.  The numbers can't skew that much, that fast.  More than a thirty percent drop\ldots''



``Coil?'' Tattletale spoke.  She looked a little pale.



``Tattletale, do you know why the numbers would change?  Does your power tell you anything?''



She shook her head, started to speak, but was interrupted.



``Then go,'' he ordered her, ordered us.  ``I will contact you later, and we will finish this conversation then.''



``I--''



``\emph{Please},'' he stressed the word, ``See yourselves out.  This situation, whatever it is, demands my attention.''



Tattletale nodded.  Together, we headed around the walkway to the door we'd come in.  We were halfway up the stairs to the hatch when Regent commented, ``Well, that was surreal.''



``Not the word I'd use to describe it,'' I replied, quiet.



``What's her deal?  Is she like Labyrinth?  Powers fucked with her head?''



I looked at the others, then turned to look at him.  I couldn't help but let a little venom seep into my voice as I asked him, ``Are you dense?''



``What?  She said she got headaches, Coil said it was hard on her, using her power, it's not a stretch of the imagination to think there's something going on mentally, especially seeing how she acted.''



``The candy she was asking for was a euphemism for drugs,'' I spoke, and saying it aloud made it somehow more real.  I hugged my arms tighter against my body, ``He's keeping her strung out so she'll cooperate, give him his numbers.''



``I don't think--''



``Shut up,'' I cut Regent off.  ``Just shut up.  I- I can't argue with you on this.  Please.''



He stopped.  I looked at the others.  Grue had his arms folded, and was standing very still.  Bitch just had her usual angry look.  Tattletale looked pale, even for the single lightbulb's worth of light we had in the stairwell.  She wouldn't meet my eyes.



``You'd know if you watched the news,'' I told Regent, ``If you read the paper.  I hate that I have to explain this, when I don't even want to \emph{think} about it.  She's the missing kid.  Remember our bank robbery?  How we were weren't even front page news because an amber alert took priority?  That was her.  Dinah Alcott.''



The revulsion and anger that was welling up in my chest and throat made me want to throw up, hit something, right there.  Some of that emotion, a lot of it, was directed at myself.  I looked to Tattletale, ``Tell me I'm wrong.  Please?''



She broke eye contact, which was answer enough.



``Get it, Regent?'' I asked him, ``The bank robbery was a distraction for the local capes, so Coil could be sure to get away with taking the kid.  We played a part in that. \emph{We} made that happen.''





