





``We're not to blame for what Coil did,'' Grue told me.



``We sure helped it happen.''



``There was no way we could know what he was really doing.''



``Because we were complacent, not paying attention.  Because of that, and because we assisted Coil in distracting the capes, Dinah has been held captive for what, three weeks?  Almost a month?''



``Almost a month,'' Tattletale echoed me.



I looked at Tattletale, noted how she was refusing to look anyone in the eye, and I had an uncomfortable thought.  ``Did you know about this?''



``I-'' She stopped to give a little sigh and briefly make eye contact with me before staring back down at the ground.  ``I had an idea, sort of.  I didn't think it would be this ugly.  It's hard to explain.''



``Try,'' I spoke, my voice hard.



``She disappeared from the middle school near Arcadia the same day we robbed the bank.  Obviously, Coil wanted to ensure the Wards weren't close enough to interfere, probably why he was so keen on us doing the bank job, after I suggested it.  I made the connection, after.  I just didn't think – Nothing he said or did led me to think it would be a serious kidnapping.''



``What else could it be?'' Grue asked her.



``Her uncle's one of the mayoral candidates in the election this Summer, you know that?  I knew Coil was putting a lot of value on getting hold of her, I thought maybe he was kidnapping her to use her to ransom for the uncle's campaign funds, or to get the uncle to drop out of the race in a more direct play.  I had a suspicion he got her to cooperate with some sort of incentive.  Figure out she's unhappy at home, give her a place to stay and some sort of bribe.  Either way, it's more fitting with his methods to date, and it would have been short term or more benign.  Not so bad.''



``Kind of off there,'' I said, bitterly.



``I'm aware,'' Tattletale answered, with just as much emotion in her voice.  ``I don't like it either.  He's been around me enough, communicated with me enough, to have an idea of stuff that I won't necessarily know or think to look for.  I didn't even know she had powers, or how Coil would have found this out or found her.  This is out of character for him.  Ruthless, power hungry.''



``If it bothers you that much, tell him to fuck off,'' Bitch cut in, sounding irritated.



``It's more complicated than that,'' I said.  ``We can't just walk away and leave her like that.''



``And some of us are kind of relying on Coil for some major stuff,'' Grue spoke.  ``Some of us have people we can't leave behind.''



I looked at him, surprised, ``I don't want to say your sister isn't important, but\ldots are you really willing to let Dinah stay in captivity, just for Aisha?''



``If it comes down to it?  Yeah.''



I stared at him.



``I'm being practical, Taylor,'' Grue lapsed into using my real name, ``People are suffering all around the world.  We ignore what's happening elsewhere every second of every day, focusing only on our country, our city, our neighborhood, or on the people we see daily.  We only really care about the pain and unhappiness of our loved ones, our friends and families, because we couldn't stay sane if we tried to support and save \emph{everyone}.  Nobody could try to do anything like that, except maybe Scion.  I'm applying that concept to a smaller scale.  My family and my team, they take priority, and they take priority in that order.  If I have to choose one way or the other, I'm going to take the option that includes Aisha and you guys.''



``This is different from ignoring starving kids in a third world country or ignoring some homeless guy on the street,'' I told him, ``You've seen Dinah in person, you've looked her in the eye.  You're already involved, you've played a role in her situation.''



``I'm not saying I like it, I am \emph{definitely }less sure I want to work with Coil, now, but I'm saying it's something that we should discuss and come to a consensus on.''



I looked at the others, ``You feel the same way?''



Bitch gave me an annoyed look.  Okay, I wasn't expecting an ally there.



Regent shrugged, ``I've told you where I come from, how I grew up.  I've seen similar stuff before, only it was my dad's powers, not drugs.  I've got a high tolerance for that shit.''



I tried to convince him, ``Didn't you leave Heartbreaker because of stuff like that?  Aren't you just getting back into the same situation with Coil?''



``I left my father because he was trying to control me and force me to be someone and something I wasn't.  It wasn't even remotely interesting or fun any more.  The day that happens with Coil, I'll leave him too.  For now, it's a good gig.''



\emph{These are the people I've been associating with?}  I looked to my last hope for a backup and support.  Tattletale.



She had her thumbs hooked into her belt, her shoulders hunched forward a little, where she leaned against the wall.  She didn't look happy.



When she met my eyes, she gave a little shake of her head.



``Coil's not stupid,'' Tattletale told me, ``He knows what he just did, he had every reason to suspect that one or two people in our group might find his methods distasteful.  He calculated this.  He's testing us, making sure we'll stick around when it's time to make the hard calls.''



``If this is a test,'' I spoke, feeling my heart sink, ``I think I fail.''



``Don't say that,'' Tattletale spoke.  ``Grue's right, we need to discuss this as a team.''



``Discuss what?  Whether to stay with Coil?''



``Yeah,'' the word was a half-sigh coming out of her mouth.



``That you guys even think it's negotiable is pretty fucked up,'' I replied.  The anger and betrayal I was feeling made my tone harsher, harder.



I don't know what I expected, but I stood there for a few seconds.  Maybe I was waiting for an apology, some sort of excuse, or an admission from them that I was right.



None of them opened their mouths to offer any of that.



I turned to leave, pushing the hatch open as I stepped back into the gravel lot that surrounded the high-rise in construction.



``Come on Taylor,'' Grue called out behind me.  I didn't listen.



``Hey!'' He raised his voice.



I didn't reply.  I was too angry, and as moronic as it sounded, I didn't want our parting words to be me cussing at him.



I was three paces away from the hatch when I heard the crunch of gravel behind me.  I wheeled around to see Grue closing the gap behind me, one arm outstretched, as if to grab me.



My temper exploded at the same time my bugs did, spilling out from beneath my costume.  At my instruction, they swept between Grue and I, creating a barrier of sorts.



I was already thinking of how I'd deal if it came down to a fight – his costume covered his skin, but I remembered the vents on the edge of his mask, that redirected the flow of his darkness from his face out the edges of his mask, so the skull image would stand out.  In a pinch, my bugs could get in that way.  His power didn't really affect me, but would a slow trickle of my bugs into his mask compensate for his obvious advantages in hand to hand fighting?



I heard the growling of Bitch's dogs.  They weren't full size, but they were bigger than normal, locked into the beginning stages of their transformations.  In the dimly lit lot of the construction area, I could see their shadows through the haze of my swarm.  Dealing with them would be hard, if not impossible.



``No,'' Grue spoke, on the other side of the swarm.  ``Fuck.  Let her go.''



I turned and fled.



\sectionbreak



The loft was empty, with only Angelica present.  Behind her, the TV had been left on, a low level of background noise and activity to reassure the dog, maybe, or just Alec being lazy about turning everything off.



Angelica moved very slowly as she climbed down from the couch and approached to investigate me.  Whatever her past experiences, she had never learned to like any humans other than Bitch, so I only got a cursory sniff before she turned to shamble back to the couch.  Whatever energy she'd expended to get to me, check me out and return to where she'd been resting, it didn't leave her with enough of a reserve of strength to hop up.  She settled down under the coffee table, watching me with her one intact eye, a perpetual wink, if winks could be wary or threatening.



Fog had done a number on her.  It was hard to believe, but she was \emph{better} than she'd been a few days ago.  Bitch had intended to use her power on the dog, but Lisa had advised against it, warning about the threat of cardiac arrest.  As a consequence, Angelica had spent the better half of a week so lethargic, weak and still that I'd frequently looked at her and wondered if she'd stopped breathing.  I wasn't so attached to her that I'd be upset if she died, but knowing how much the loss of a dog would gut Bitch had given me enough of a reason to worry about the critter.



It was strange to think I was walking away from this: the loft, the dogs, and the others.



I didn't know how to parse what I was feeling or thinking.  I felt angry, betrayed.  Standing in the living room of the loft, the feeling of being lost was particularly keen.  I didn't have a plan, and I'd had a plan for a while, now.  For my first year and a half of High School, it had been all about getting through to the end of the day, reaching the weekend.  When the weekend came, it was about recuperating, rebuilding my mental and emotional strength to face the coming week.



Then I had gotten my powers.  I'd reached my very limit, the moment I might have cracked, and my powers had given me something else to strive for; being a superhero.  There'd been so much to do, so much to plan, prepare and research, that it had given me a reason.  I was hesitant to define it as hope, but it had given me something to focus on beyond the next twenty four hours.



Everything else had flowed from that point.  Meeting the Undersiders, committing to a new plan as an undercover agent, with a new goal of getting info on them and their then-anonymous boss.  When I couldn't do that in good conscience, I changed my plan to getting to know the others, being a friend to Bitch, bonding with Brian.  Admittedly, I'd had varying degrees of success, in the short period I'd traveled that road, but it had been enough for the present.



And now I was adrift.



I was, in a way, back to square one.  I had to get through today, then get through this week.  I'd figure out where to go from there.  I headed to my room.



My backpack sat beside my bedside table, and a quick investigation revealed it still contained a lot of what I'd stashed in there a week ago, back when I'd expected to spend a few days at Brian's.  Clothes, basic toiletries, cash, an unused disposable phone.  I added more money, the card with the info for my supervillain bank account, and a few more things.  Checking the room for anything I thought I might need, I found myself looking at my dresser.  Resting on top were the katana I'd claimed as a prize from one fight, and the piece of amber Brian had given me.



I stuck the amber in my bag, surrounding it with clothes to pad it, and then zipped it up.



The alarm clock marked the time at 6:40 in the morning.  If Coil hadn't called for the meeting at this strange hour, if I hadn't been packing, this would be about the time that I headed out the door for my morning run.



Leaving like I was, hurrying to be gone before the others caught up with me, I was leaving a lot of stuff behind.  Clothes, furniture, pictures.  Without even realizing it, I'd sort of begun making this space my own, decorating and personalizing it.  Settling in, in a way I hadn't when I'd been planning to betray the group.



I was putting clothes on over my costume when Lisa's voice came from the doorway, ``Where are you going to go?''



I turned to look at her, and her expression changed.  Was it the look on my face?  I wasn't sure what emotion I was conveying.  Anger?  Disappointment?  Regret?



``A motel, maybe,'' I said.  ``Why?  Are you going to have to hunt me down?  Tie up a loose end?''



``You know we wouldn't.''



``Sure.  I suppose he'll send the Travelers after me if he goes that route.''  I pulled my mask off and put it away in the backpack.



``This feels bad, Taylor.  You really have to go?''



``I don't even want to look at \emph{myself} in the mirror, right now.  Even if we came to some sort of agreement, made a plan to save her together, go against Coil\ldots'' I trailed off, trying to find the words, ``I can't face everyone else and pretend like things are normal.  Even if we were working to save her\ldots it feels disrespectful.  Dinah deserves better than that.''



``Believe it or not, Brian's as freaked out as you are.  If he's being weird or out of character, it's just him defaulting to his core programming, you know what I mean?  Like Bitch getting angry, or you going quiet and wary.''



I shrugged, tied my sweatshirt around my waist, told her, ``In hindsight, I don't think it \emph{was} that out of character for him.  Part of the reason I'm leaving.''



``Is this leave permanent or temporary?''



``Don't know.''



``Are you going to do something stupid like try to rescue Dinah yourself?''



``Don't know,'' I repeated myself.



``You're aware that there's an outside chance that if you try, we might have to try and stop you.  Depending on what agreement the rest of us come to about the current sitch.''



``Do what you have to, I'll do the same.''



``Alright, then.''



I slung the bag over my shoulder, faced the door.



Tattletale spoke, ``I'm not saying goodbye, because this isn't.  I'll resolve this situation with Coil and his captive myself, if I have to, if it means we can have another civil conversation in the near future.  Stay alive, don't do anything rash, and be open to hearing us out in the future?  Surely our friendship is worth doing that much?''



After a moment, then I gave her a single nod.



Lisa moved out of the doorway to let me through.  When I turned in the direction of the living room and the stairwell, Lisa almost deliberately turned in the other direction, toward the kitchen.  As if following me to the exit constituted some vague sort of farewell, and she was sticking to the idea of refusing to say goodbye.



I was halfway down the stairwell to the first floor when I heard it.  A whining noise, like you might hear from a particularly large baby preparing to scream.  The nasal `wa' sound stretched out, so loud it was painful to listen to.  A siren?  An air raid siren.



I reversed direction and ran back up the stairs.  Tattletale was already in the living room.  The TV was showing evacuation directions in a rotation of images:  Leave your homes.  Find the nearest shelter.  Follow the directions of local authorities.  Leave your homes\ldots



``Bomb?'' I asked, raising my voice to be heard over the siren, ``Bakuda leave something behind?''



Lisa shook her head.



I'd seen her in the presence of Lung, around Glory Girl, Bakuda, Purity, Night and Fog.  Looking at her, now, I saw an expression on her face that I hadn't seen in any of those scenarios.  There was no trace of her vulpine grin, none of her characteristic humor or reckless abandon.



``Then what is it?''  I asked her, though I already had a dark suspicion.  Even the Bakuda's terrorism campaign against the city hadn't warranted the sirens, and that left very few possibilities.



Her response was one word, final. ``Endbringer.''



``What- but-''  I turned toward the stairs, then back to Tattletale, ``My dad.  I've got to-''



Tattletale cut me off, ``He'll evacuate or get to a shelter like everyone else.  Taylor, look at me.''



I did.



``The others and I, we talked about this possibility.  It came up before we met you.  You listening to me?  You know what happens, the usual response.''



I nodded.



``We all decided we'd go.  That we'd try to help, however we could.  But you weren't a part of that talk, and there's tensions in the group.  You're pretty much not on the team, right now, so if you don't want to-''



``I'll go.''  I didn't even need to think about it.  I would never be able to forgive myself if I walked away, knowing there was something I could have done to help.





