
<Walk!> the soldier barked in Turkish.  He jammed his gun between her shoulderblades, hard.  He was twice as tall as her, far stronger than her, so there could be no fighting or resisting even if he wasn't armed.  She stumbled forward into the shrubbery and trees, and branches scraped against her forearms and face.



\emph{One foot in front of the other, }Hana told herself.  Her feet were like lead weights as she trudged forward.  The needles on the trees and shrubbery scraped against her skin.  Even the twigs were coarse, almost thorny, catching on her dress and socks, biting through the cloth to scrape her skin and stab at her shoeless feet.



<Faster!> the soldier threatened.  He said something else, longer and more complicated, but Hana's Turkish wasn't good enough to make it out.  She looked over her shoulder and saw the man back the way she'd come.  He made his meaning explicitly clear by waving his gun toward the other children, who were corralled in the midst of a half dozen other soldiers.  If she didn't move faster, someone else would pay for it.



Seven years had given her village false confidence, let them believe that they were far enough away, secluded enough in the valley and forest, that they could escape the worst fighting of the ongoing war.  That illusion had been shattered just hours ago.



She had been hidden in the cellar beside her house.  She had heard the screams and gunfire.  Too much gunfire, considering how few working guns the men and women of her village had.  Guns and bullets were too expensive when you lived off your garden and what you could hunt, and a trip to the nearest city to buy such things was dangerous.  What they had were the leftovers, the handful of weapons taken off enemies by the guerilla fighters and left behind or traded in barter when they passed through the village for supplies and medical care.  Those who had the guns lacked the skill or training to use them.  The fighters were supposed to defend them against people like this, stop them from getting this far.



She hurried to take another step forward and flinched as a twig broke underfoot.  The smallest of whimpers escaped through her lips.



When the enemy soldiers had found her in the cellar, dragged her into a group with the nine other children of her village, she'd known that her parents were already dead or dying.  As the soldiers had marched them through the village and into the woods, she'd stared hard at the ground, tears streaming down her cheeks, unwilling to look at the blood, the bodies, that littered her hometown.  People who she had seen every day of her life.



Her eyes scanned the forest floor, but she had no idea what to look for.  A hump of earth?  Twine?  A dense patch of dry, brown needles?  She took another step forward, waited for disaster.  When it didn't come, she stepped forward again, paused.



Only a short while ago, she had watched from a distance as Kovan, the fat older boy that had once called her names, stepped forward and had his leg fall into a hole.  He'd screamed, and when Hana and the rest of the children had rushed forward to try and lift him out, they had only increased the volume of his shouts and the ferocity of his thrashing.  With the Turkish soldiers watching silently behind them, Hana and the others had used their hands to scrape at the hard, rocky earth, revealing the wooden stakes that were lodged in the sides of the hole.  Each was set in the earth so they pointed downward at an angle, with some at the bottom to pierce his foot.  Supple, the wood had bent enough to let the leg fall down deep into the hole, but attempts to raise Kovan had only pulled his leg and foot up into waiting wooden points.



It was, she knew, one of the traps that had been placed by her village's hunters or by the guerrilla fighters that defended their village.  They were all over, set throughout the woods, around her village, near roads and other important places.  She had overheard one of the fighters describing this very trap to her father.  She had been told, over and over, that she wasn't to play in the woods for much this reason, that if she had to travel into the woods for any reason, she needed an adult to guide her.  The full reality of it hadn't registered until she saw what had happened to Kovan.



They had tried for a long time to dig the boy's leg free, knowing as they uncovered more and more of his pierced leg, saw the injuries and the quantity of blood, that he wasn't going to be able to walk very far.  It was hopeless, they knew, but Kovan was someone they had gone to school with.  Someone they had seen every day.



A soldier had put an end to their efforts with a bullet through Kovan's head, making Kovan the second of the children to die.



Hana was picked to go next.  To test the path.



She clutched the front of her dress, balling the fabric up in hands that were still covered in dirt and scrapes from her efforts to dig Kovan free.  \emph{One}\emph{foot in front of the other}.   Every single one of her senses was on edge.  She was hyperaware of the rustle of dirt underfoot, the scrape of pine needles against the fabric of her dress.  She could feel the warmth of the sun heating her skin when she stepped into a spot where the light filtered through the pine trees.



She blinked hard to clear her eyes of tears.  So stupid.  She needed to be able to see.  Any clue.  Any at all, to see a trap.  Crying was the worst thing she could do.



\emph{One foot in front of the other.}



She stopped.  Her feet refused to go any further.  Trembling, she looked around.



If she took one more step, she \emph{knew}, she was going to die.



There was no rationale for it, no reason or clue.  This patch of forest was no different from the rest.  A bed of red-brown needles underfoot, shrubs and trees pressing in around her.



But she \emph{knew}. \emph{ }Whether she took a step forward, to her right or left, she would be stepping into a trap.  A hole like the one that caught Kovan, or perhaps an explosive device, like the one that took Ashti.  At least she'd gone quickly.



The soldier that was watching her called out from a distance behind her, the ever familiar <Walk!> that was a threat and an order at the same time.



Sick with fear, Hana looked around, searching for something that could tell her where to go, how to move.



In that moment, she knew she wasn't going to die right away.  She couldn't walk any further, it was physically impossible, as though her feet were as rooted to the ground as the trees were.  They would make her watch as they tortured one of the other children to death.  Then they would start on the next, maybe Hana herself, until they had another child willing to act as decoy and clear the traps from their way in the simplest, most dangerous manner possible.



<Wal-



She saw something vast.



It wasn't big in the sense that the trees or even the mountains were big.  It was big in the way that transcended what she could even see or feel.  It was like seeing something bigger than the whole wide planet, except \emph{more – }this\emph{ }thing that was too large to comprehend to start with, it extended.  She didn't have a better word to describe what she was perceiving.  It was as though there were mirror images of it, but each image existed in the same place, some moving differently, and sometimes, very rarely, one image came in contact with with something that the others didn't.  Each of the images was as real and concrete as the others.  And this made it big in a way that she couldn't describe if she were a hundred year old scholar or philosopher with access to the best libraries in the world.



And it was \emph{alive}.  A living thing.



She knew without having to think about it, each of those echoes or extensions of the entity was as much a part of a connected whole as her hand or nose was to her.  Each was something this living entity was aware of, controlled and moved with intent and purpose.  As though it existed and extended into those possible selves all at once.



\emph{It's dying}, she thought.  The outermost extensions of the creature were flaking off and breaking into fragments as it swam through an emptiness without air, not moving but sinuously adjusting its self through the existences that held the echoes, shrinking away here and swelling there, carrying itself away at a speed that outpaced light.  In its wake, flakes and fragments sloughed off of the entity like seeds from an impossibly large \emph{karahindiba}, or dandelion, in a steady wind.  Seeds more numerous than all the specks of dirt across all the Earth.



One of those fragments seemed to grow, getting bigger, larger, looming in her consciousness until it was all she could perceive, as though the moon was falling, colliding with the earth.  Falling directly on top of her.



-k!> the soldier finished without missing a beat.



Hana stirred, she was still in the forest, hands stinging with the scrapes, feet sore from the walking.  Her heart pounded and she could taste fear like bile in her mouth.



Already, the memory was fading.  Had it even happened?  As hard as she struggled to retain it, it was eluding her.  It was like a dream that escaped her when she woke, but so slippery that even the idea that she'd dreamed in the first place was quickly retreating from her mind.



The soldier shouted something too complex for her to understand, directed at his comrades.  Hana let the scraps of the memory slip from her attention.  This, here, was the priority.  Either she walked forward, and she would die, or she would stand by and watch the others die for her cowardice.  With just the vestige of an idea that something had happened, she had been shaken from her paralysis.  Maybe she could step forward.



She raised her foot-



And stopped.  Something stood in her way.  A blur hung in the air at chest level, crackling, shifting with a manic ferocity.  She let her foot fall back down where it had been a moment ago and stared at the kaleidoscopic shimmer of black and green.



She touched it, and felt a weight settle into her palm.  Her hand automatically closed around it, feeling the warmth of it.  It felt almost like when she pet a friendly dog.  An odd thought, given what she found herself looking at.



A gun, polished gray steel.  Somehow familiar.  Identical to the smallest guns she had seen the guerrilla fighters carrying.



\emph{I can't use this}.  The thought was cold in her mind.  \emph{If I use this, they'll kill the others the second I fire.}



The gun shimmered, became that blur of green and black, then settled into a new shape.  She'd seen this, too.  One of the fighters had been talking to Hana, showing her his English gun magazine, in an effort to get in good graces with her older sister.  This was similar to the gun she'd just had in her hand, but there was a metal tube on the front, nearly doubling the gun's length.  The tube, she knew, made guns quieter.



The rest of the children and the other soldiers were far behind.  It was still nearly impossible, but-



<Walk!> the soldier behind her shouted.  <Walk or->



She wheeled around, holding the gun in both hands.  She took a second to steady her aim, and the Turkish soldier's surprise bought her just enough time to pull the trigger.



Hannah's eyes snapped open.



\emph{This is why I don't sleep.}



She was still wearing her costume, she noted, as she rose from her bed and walked to the bathroom.  At least she'd had the sense to remove her scarf so she didn't strangle while she rested.



She was the only one who remembered.  Everyone else forgot that impossibly huge being, if they were even graced with a glimpse of it.  She couldn't be sure.  If any others saw it, they would inevitably forget it before they could gather their thoughts enough to speak of it.  Like she was supposed to.



But she remembered.  She touched the combat knife that was sheathed at her hip, as if to remind herself it was there.  She harbored her suspicions about her gift: her powers had taken a part of her psyche and given it concrete form.  The angriest parts of her, the most childish parts, the parts of her that dreamed, and those that forgot.  The knife at her hip slept for her and dreamed for her, she imagined.  She had gone nearly a year at a time without needing to stop and put her head to rest on a pillow.



When she closed her eyes and let herself drift off, it was because she felt it was something she \emph{ought} to do, not because she had to.  Even then, she never dreamed.  She remembered, instead, her mind replaying past events in perfect detail.  And through some chance of fate, this meant she remembered the entity, and she remembered forgetting it, as paradoxical as that was.



And she would never speak of it to anyone.



She'd killed the soldiers that held the other children of her village hostage.  After the first, she had feigned fear, pretended the guerrilla fighters were in the woods.  Then she had waited for the moment they were too busy watching the woods and mowed the rest of the men down with an assault rifle.  She didn't even feel bad about it, nor did she lose much sleep that one of the children, Behar, had been shot in the skirmish.



She regretted the deaths, that went without saying, but she didn't feel guilty about it.  Of the ten of them, seven had made it back, because of her and her gift.  They had returned to their village, moved the bodies out of sight, and did what they could to conserve their food until the guerrilla fighters came through once again.



Hana had made the others swear a promise, to not speak of her gift.  She knew the guerrilla fighters would recruit her, use her, if they knew.  Whatever this power was that she had received, she didn't feel it was for that.



When the fighters had returned, they saw the state of the children and elected to evacuate them.  The fighters took them to a city, and a man there saw that Hana and the others were shipped off to the United Kingdom, where many other refugees were going.  They were split up, and the others were sent one by one to homes for orphans and other troubled children.  Hana's turn came late, nearly last, and she was taken to fly on another airplane to her own new home.  It was there she ran into difficulty.  She'd moved through the archway – what she would later learn was a metal detector – and it sounded an alarm.  Guards had found the weapon she couldn't drop or leave behind, and Hana was carried off to another place.  Interrogated, asked many questions.  She was taken to the bathroom, patted down on her re-entry to the interrogation room, and they found the same gun on her that they'd taken away just half an hour ago.



Everything else had happened very fast, after that.  It was an American in a military uniform that rescued her.  He took her to America, saw that she was put with a family there.  When the first three Wards teams were established, she was enlisted.  She barely knew a hundred words of English, her numbers and the alphabet, when she first went out in costume.



Hannah bent over the sink and washed her face.  She found a toothbrush and cleaned her teeth, then flossed, then scraped her tongue.  Too easy to forget those things, without the rhythm of sleep to break up the continuity of days.  Better to do these things a little too often, than to forget.  She gargled with mouthwash, then bared her teeth to see the dentist's work, where he had capped them.  Teeth that were perfectly shaped, white.  Not really hers.



Her weapon found its way into her hand at some point after she put the mouthwash down, a handgun not unlike the first shape it had taken for her.  She spun it around her finger by the trigger guard a few times before holstering it as she left the bathroom.  She went to the window and stared at the city across the water.  Colors shifted subtly in the refracted light of the PHQ's forcefield, oversaturating the view like a TV with bad picture settings.



Even if she never dreamed, America still had a surreal, dreamlike quality to it.  It was so distant from where she had come from, so different.  There was no war here, not really, and yet the people here managed to find so much to  complain about.  Men in suits, trouble in love, medical care and not having the latest touchscreen phone.  Such complaints often carried more emotion and fervor than anyone in her village had used to bemoan the death of loved ones or the methodical eradication of their people.  When she heard the complaints of her friends and coworkers, she simply nodded and gave the necessary words of sympathy.



Bright lights and conveniences and wanting for nothing and televisions and sports cars and capped teeth and chocolate and the list went on\ldots  It had taken her the better part of a decade to even start getting used to it, and everything moved so fast that any time she thought she was getting a grasp on it, there was something new, something she was supposed to know or understand.



She'd accepted without complaint when her adoptive parents told her to start writing her name in the more American `Hannah'.  She'd agreed and signed the papers when they took the last name her parents had given her and replaced it with their own. Small things, so minor, compared to what she had seen and done.  It didn't bear complaining about.  Everyone praised her for how dutiful she was in school and her training.  She never gave up, never quit.  Why should she?  This was nothing compared to those hours she spent in that forest.



So hard to believe that the events from her dream had occurred just twenty six years ago.



It never felt entirely real.  More than once, she had let herself begin to believe she'd died, that she'd taken that step forward and never made it out of the forest.  She had made mistakes when she let herself think that way, had put herself in too much danger, back in her earliest years as a hero.  Now, when she found herself slipping into that mindset, she often tried to sleep.  Her memories as she slept were perfect, unblemished, almost more real than real life, which was why she never did it too often.  Ironic, given how necessary it often was, to keep her grounded in reality.



She'd grown to love this country.  Truly love it, for what it stood for.  She'd had to fight to wear the flag as part of her costume.  America wasn't perfect, but nothing touched by human hands could be.  There was greed, corruption, selfishness, pettiness, hatred.  But there were good things too.  Freedoms, ideas, choices, hope and the possibility that anyone could be anything, here, if they were willing to strive for it.  As she accepted her new country, she let herself make friends, boyfriends, let herself get close to her parents and their church.  By the time she started college, her accent had all but disappeared, and she knew enough to at least pretend to know what others were talking about when they spoke of pop culture, music and television.



People were judgmental, she knew, and so she would never speak of what she had seen in that moment she received her gift.



Even among other faithful, she would be met with suspicion and scorn, were she to say she'd seen God, or one of His warrior angels, such as they existed beyond the scope of human understanding.  That He had given her this ability so she could save herself.  Others would offer different interpretations, argue that He had given such gifts to bad people, too, they would point to the science of it.  Maybe some small part of her suspected these hypothetical individuals were right.  Still, she preferred her faith to uncertainty.  The notion that this thing she had seen was something other than a benign entity watching over humanity, that it might be malign, or even worse, that it existed with no conception of the effect it had on mankind?  An elephant among gnats?  It wasn't a comfortable thought.



She glanced at the clock; 6:30 in the morning.  She draped her flag-printed scarf loosely around her neck and lower face, then left her room.  The energy became an assault rifle hanging at her side, bouncing a comforting beat against her hip as she walked. She made her way up a flight of stairs and down to the end of a hallway.



She heard a male voice, a female one.  She paused at the open doorway and knocked.



``Yeah?'' Armsmaster called out.



``Am I interrupting?''



``No.  Come on in,'' he replied.



She stepped into the room.  It fell somewhere between a workshop and an office.  Two spare suits stood at one side of the room, each with minor functional differences.  A set of Halberds were placed on a rack behind Armsmaster's desk, one shattered in pieces.  One of the spaces on the rack was empty – Armsmaster had the Halberd in front of him.



``You worked too hard and forgot to go to sleep again, Colin?'' Hannah asked, though the answer was obvious.



He frowned, reached over to his computer and hit a button.  He saw the time, muttered, ``Damn it.''



``Good morning, Miss Militia,'' a woman's voice came from the computer.



Hannah blinked in surprise, ``Dragon.  Sorry, I didn't realize you were there.  Good morning.''



``You're up early,'' Dragon commented. ``And you were out late, from what I'm seeing on the web.  Trouble sleeping?''



``I don't sleep,'' Hannah confessed.  ``Not really, since I got my powers.''



``Oh?  Me either.''



Colin leaned back and rubbed his eyes with the heels of his hands, ``I'd give my left foot for that little perk.''



Hannah nodded.  There were others like her?  She asked the computer screen, ``Do you remember?''



``Sorry?  I don't understand,'' Dragon replied.



``Nevermind.''  If Dragon \emph{did} remember, Hannah knew the answer to that question would have been different.  Dragon was too smart to miss the connection.



``We were talking shop,'' Colin spoke.  He motioned to the Halberd he had in front of him.  ``Procrastination through Tinker stuff.  I think tonight's project was a success.''



``Oh?''



Armsmaster stood, seizing the Halberd in one hand.  He pressed a button on the handle, and the blade blurred.  Without even swinging the weapon, he let the heavier top end fall against an empty stainless steel mannequin that might have held a spare suit of his armor.  Dust blossomed where the blade touched the mannequin, and it passed through without resistance.  Pieces of the mannequin clattered to the ground.



``Impressive,'' she told him.



He pressed a button, and the blur around the blade dissipated in a steel-colored smoke, leaving only the normal axehead top of the weapon.



``Only problems are that it's vulnerable to forcefields, fire, and other intense energy, and the apparatus takes up too much space in the upper end.  Even with my power, it likely means I'd have to do without some of the kit I've gotten used to.''



``I trust you'll figure it out,'' Hannah told him.  Then with mock sternness, she put her hands on her hips, ``Now, no more distracting me.  Just what are you procrastinating on?''



Colin ran one of his hands over his short cropped brown hair, sighed.  ``Right.  You have as much say as I do, in this.''



He walked back to his desk and slumped down into his seat.  He kicked a screwdriver and a pair of pliers from the corner of the desk to put his feet up, one ankle crossed over the other.  Reaching in the opposite direction, he grabbed a stack of folders and let them fall to the desk.



``Piggot has decided to take action in reflection of recent events.  Both the Wards and the Protectorate are being restructured.''



Hannah winced, ``How bad?''



Shrugging, Colin told her, ``As far as the Wards go, we're losing Aegis.  Piggot and the PRT want to see how he does leading a different team, and the boy's parents are amenable.  He'll stay in the Wards for a little longer, to suggest he's younger than he is.''



``A shame.  Who do we get?''



``It's a swap.  It'll be Weld from the Boston team.''



``I don't know him,'' Hannah admitted.



``He's a good kid with a good record,'' Dragon chimed in from the computer, ``Ferrous biology, absorbs metals through his skin.  Strong, tough, good grades across the board, high marks in the tactics simulations.  Likable, and a scan of the web shows feedback for him is higher than average, which is impressive, considering he's one of the Case 53s.''



``He's got the tattoo?'' Hannah asked.



``The mark is branded into his heel, not tattooed, but yes.''



Hannah nodded.  ``What else?''



Colin frowned, ``We're supposed to pick two others from our Wards team to transfer to one of the other major teams, nearby.  I settled on Kid Win, I'm stuck on the others.''



``Browbeat?''



``Too new.  Might be able to sell it to Piggot, but my suspicion is that she'll think it looks bad, giving up our newbie.''



``Hm.  Gallant won't be able to leave for Boston.  Too many logistical issues,'' Hannah glanced at the computer.  She couldn't say more.



``You can speak freely,'' Colin spoke, ``Dragon has either read the record in question, or she's reading it as we speak.''



``Gallant has local responsibilities, and is expected to start helping with his father's local business enterprise,'' Dragon spoke, giving truth to Colin's words, ``Miss Militia is right, he's a local fixture.  And his girlfriend is here.''



Hannah nodded, ``Painful to give up Vista or Clockblocker.  They're our big guns, and they're local heroes after the role they played in that bomb scare.  Shadow Stalker?''



Colin shook his head, ``There would be more trouble over handing over someone like Shadow Stalker to another team than there would be if we gave away a newbie like Browbeat.  Discipline problems.''



``Still?'' she asked.  Armsmaster nodded.



Hannah frowned, ``Alright.  This is what you do, then.  Propose Shadow Stalker and Kid Win.  If Piggot does refuse Shadow Stalker, and you should make an argument that Shadow Stalker might need a change of scenery, Piggot will have a harder time refusing Browbeat, right after.''



Colin rubbed his chin, where his beard traced the edges of his jaw, nodded.



``If she doesn't agree to giving away either of the two, and you really should play hardball on that, you can offer Clockblocker.  He graduates this summer, anyways, and I'd say he's got enough friends and contacts here that he might apply to come back to Brockton Bay to join our Protectorate when he turns eighteen.  Best case scenario for us, and it's not like Boston or New York need more capes.''



Colin sighed, ``You're better at this than I ever was.''



Hannah wasn't sure how to respond.  Colin had his strengths, but he was right.



He went on, ``Congratulations.''  He picked up the second folder and held it out to her.



``What?''  She took it, opened it.



``There's a change to our team, too, according to Piggot and the rest of the oversight.  You've been promoted.  Within the next two weeks, this building and this team will be transferred to your command.''



She stood there, paging through the folder of paperwork, stunned.  ``Where are you going?''



``Chicago.''



Hannah broke into a smile, ``Chicago!  That's fantastic!  A bigger city, a bigger team!  Where's Myrddin being moved?''



``He stays in Chicago.''



Hannah shook her head, ``But\ldots'' she trailed off.



The hard look on Colin's face was telling enough.



``I'm so sorry,'' she spoke.



``It's the politics,'' Colin spoke, leaning back, ``I'm good at this.  Better than most, if you don't mind me boasting.  Everything I bring to the table, I worked my ass off for.  But when it comes to shaking hands, managing people, navigating the bureaucracy\ldots I'm not good at it, won't ever be.  Because of that, I'm getting demoted, and I can probably give up on ever being in charge of another team.''



``I'm sorry.  I know how much you wanted-''



``It's fine,'' he said, but it was clear in the curtness and hardness of his tone that it wasn't.  He turned away and touched his keyboard.  In the darkness of the room, his face briefly reflected the blue light of the screen.  His brow furrowed.



``Dragon.  That program you gave me, predicting the patterns of class S threats, remember it?  I made a few modifications, to see if I couldn't catch any highlights, I'm running a dozen of them concurrently.  One, I called HS203.  I want you to look directly at this.  I've put it behind some pretty heavy security, but if you wait a second, I'll-''



``I'm already looking over it,'' Dragon interrupted.  ``I see what you did.  Linking my data to atmospheric shifts.  I think I see it.''



Hannah walked around the desk and leaned over Colin's shoulder to see the screen.  A map of the east coast was superimposed with a rainbow hued cloud.  ``This doesn't mean anything to me.''



``Nothing's truly random,'' Colin explained, his voice tight, ``Any data shows a pattern eventually, if you dig deep enough.  Dragon started work on an early warning system for the Endbringers, to see if we can't anticipate where they'll strike next, prepare to some degree.  We know there's some rules they follow, though we don't know why.  They come one at a time, months apart, rarely hitting the same area twice in a short span of time.  We know they're drawn to areas where they perceive vulnerability, where they think they can cause the most damage.  Nuclear reactors, the Birdcage, places recently hit by natural disasters\ldots''



He clicked the mouse, and the image zoomed in on a section of the coastline.



``\ldots{}Or ongoing conflict,'' Hannah finished for him, her eyes widening.  ``The ABB, Empire Eighty-Eight, the fighting \emph{here?} It's coming \emph{here}? \emph{Now?}''



Colin didn't have a reply for her.  ``Dragon?  Brockton Bay falls within the predicted zone, and the city \emph{is} on the list of locations that rate high enough on the sensitivity or negative media scale.  Add my data, the correlations between abrupt microshifts in temperature, air pressure and-''



``The data is good.'' Dragon's voice, synthesized to mask the most telling details about her identity, held no trace of doubt.



``Good enough to call for help?''



``Good enough.''



Colin moved quickly, spinning in his chair to reach a small console.  He opened a glass panel and flipped a switch.  Air raid sirens immediately began their ominous whine.



``Dragon, I'll contact Piggot and the Protectorate teams.  You get hold of everyone else that matters.  You know who's most needed.''



``Already on it.''



He turned to Hannah, and their eyes met briefly.  Much was communicated between them in that moment, and she wasn't sure she liked what she saw in his eyes.



A glimmer of hope?



``Miss Militia.  Recruit the locals.  And we need a place to gather.''



She swallowed her concerns.  ``Yes sir!''





