





The first beetle gripped the corner of the paper in his mandibles and slowly pulled it back.  Two more moved to the edges of the folds and held them firm.  The fourth and largest of the four beetles ran its head left and right along the paper until it was firmly creased.  Each of the four changed positions and repeated the steps at a different point.



``That's really creepy to watch,'' Charlotte said, from where she sat at the kitchen table.



I looked up from the laptop I was using to view a webpage on origami.  ``Is it?  I'm pretty used to them, so I don't give it a lot of thought.''



``They're so organized and human.  Bugs shouldn't act that way.''



``I don't really believe in thinking that way anymore,'' I said, absently.



``What way?''



I had to stop to compose my thoughts.  I glanced at Charlotte, and Sierra, who was standing by the fridge, silently eating her breakfast.  ``I don't believe in \emph{shouldn't}, like there's some universal rules about the way things should be, the way people should act.''



``So there's no right or wrong?  People and animals should do whatever?''



``No, there's always going to be consequences.  Believe me when I say I know about that.  But I do think there's always going to be extenuating circumstances, where a lot of things we normally assume are \emph{wrong }become excusable.''



``Like rape?  Are you going to tell me there's a situation where rape is okay?''  Charlotte asked.  I would have thought I'd touched on a hot subject if her voice wasn't so level.



I shook my head.  ``No.  I know some things are never excusable.''



``Right.''



``But as far as \emph{bugs} are concerned, at least, I figure anything goes.''



``It's still creepy.''



``Give it time.  You'll get used to it.''  I picked up the tightly folded piece of paper that was the end result of my little experiment.  I pushed at two corners of the tight paper square, and it settled into a cube about three-quarters of an inch on each side, with holes on two opposing faces.



I directed a housefly into one hole and settled it inside, then fed a braided length of twine through the holes.  I handed the result to Charlotte and ordered the bugs to start making another.



``A necklace?''  Sierra asked.  She put her plate down in the sink and ran water over it.



``Or bracelet, or a key chain.  So long as you have this, I'll know where you are, because I can keep an eye out for the fly in a box.  The \emph{real} purpose of this, though, is when there's an emergency.  You can crush the box and the bug inside, and the moment that happens, I''ll use my power to protect you.  It won't be instantaneous, but you'll have a swarm descending on whoever is giving you trouble in anywhere from fifteen seconds to a minute.  If it works out, I can make something a little more stylish for the future.''



There were nods from both of them.



``I can't protect you from a bullet or a knife wound, but I \emph{can} screen the people in your vicinity, feeling them out to see if they have weapons on them and give you a heads up so you don't get in that situation to begin with.  If there's potential trouble like that, I'll warn you by drawing this symbol with my bugs\ldots''



I drew three lines that crossed in the center, using the flies and beetles that were working on a cube for Sierra.



``Okay,'' Charlotte said.  Sierra nodded.



I got the bugs working on the second cube again.  ``I'll use numbers to inform you on the number of people nearby.  You'll want to approach a situation differently if there's twenty people than if there's five.  Maybe have one of you hang back and be in a position to crush the cube, or just keeping your distance.  Or just avoid the situation.  Trust your gut, use your best judgement.''



``What exactly are we doing?''



``For now, just door to door.  I'm going to mark the places you should visit, where there are families or groups of people.  I need the info I can't get with my bugs.  Who are the people in my territory?  What do they need: Maybe medical care, clothes, more food, maybe someone's giving them trouble?  You find out, take notes, then pass that information to me.''



``That's it?''



``For now.  I'm going to ask you guys to travel as a pair, obviously.  You'll be safer and there's a better chance you'll be able to signal me with the necklace if something goes wrong.  Not that you \emph{should} need the cube, but I prefer having some redundancy.''



The pair nodded.  Sierra bent over to pull on the rain boots I'd provided her.  Charlotte was already wearing hers.



``That's the general plan.  We'll work out other tasks and maybe other signals later, in case you need my attention but not for an emergency, or if you want to cancel a request for help, whatever.  That leaves payment.''



``I was wondering about that,'' Charlotte said.  ``But didn't know how to ask.''



``We'll try for six to eight hours a day, five days a week, but consider it flexible.  Not to spook you or anything, but I'll know if you're slacking.  I'm thinking two hundred and fifty dollars a day, and obviously it's under the table, so you're not getting taxed on it.''



``That's a little more generous than I was expecting,'' Sierra said.



I didn't like Coil, pretty much despised his methods, but I \emph{did} agree with his sensibilities on some things, like personnel and making sure people \emph{wanted} to work for you.  It wasn't like I couldn't afford it.  I had yet to spend the earnings from any of my earlier villainous stints, since Coil was providing everything major I needed.



``There's another reason I'm putting you guys out there.  Two people aren't going to be enough for what I'm planning long-term.  I want you two to trust your guts on this, but you're also going to be keeping an eye out for possible recruits.''



``You're hiring others?'' Charlotte asked.



I nodded.  ``I'm looking for people who are young, reasonably fit, and able to follow orders.  With you two out there, I'm hoping others see a pair of girls who are secure, happy and healthy in my employ.  You recruit someone I decide is worth keeping?  I'll reward you.  But this isn't a competition, got it?''



Both girls nodded their heads.



``If you don't have any questions--''



``I do,'' Charlotte piped up.  ``Do you have a mask I could wear?''



I frowned.  ``I was hoping you guys would put a more human, less sinister face on things.''



``I don't want to run into someone I know and have to explain.  Not that I think anyone I know lives around here, but--''



``Okay, no, I wouldn't expect you guys to go unmasked when I won't.  That wouldn't be fair.  Give me a few seconds,'' I told them.  I headed upstairs to my office.



Over the past few days, I'd received deliveries of the more specific and obscure items I had requested from Coil.  Among them were cases of more exotic bugs, a sturdy work table I kept upstairs in my room and five mannequins with custom measurements.



Coil's people had taken the time with Brian, Lisa, Alec and Aisha to get comprehensive measurements and hand casts.  Bitch had refused.  This had led in turn to the creation of the mannequins, which had been shipped to me and set up on the pedestals beneath the shuttered window.  One mannequin for each of my teammates and one for me.  There was also a little folder of notes from each of the others on what they wanted, including some photos, clippings and print-outs for reference.  Grue had included pictures of the little statuette he had bought at the Market, which he wanted me to copy for his new mask. I hoped to have a costume for each of us in short order.



I'd already finished a few draft attempts at designing Lisa's mask, since it didn't require much cloth and the nuances of it were tricky.  The way her old mask fit her, it hid her freckles and eyebrows and changed the apparent angles of her eyes and cheekbones so her entire face had a different look to it.  Emulating that was hard, since the texture of the silk compared to the material of her mask didn't let me copy it over exactly.  I'd used the scrapped attempts to test different dyes and how they reacted with the fabric.  I grabbed the failed masks, pressing each against a white piece of paper to ensure they weren't going to stain skin, and then headed back downstairs.



``Got black, more black, dark purple, blue and blotchy crimson.  Take your pick.''



Charlotte took a black mask that would cover her eyes and the lower half of her face, adjusted it until the eyeholes were in place, and then set about fixing her hair.



``Sierra?''



``Not much point.  My hair is pretty recognizable,'' she flicked one of her dreadlocks.



``Won't do any harm.''



She took the second, smaller black mask.  While she put it on, I deposited a fly and threaded twine into the second origami cube so she had her emergency signal.



``Good luck,'' I told them, grabbing two black clipboards with attached notepads and handing them over.  ``Come back around noon, we'll eat, and you can give me an update on how things are going.''



``Will do,'' Sierra replied.



My minions moved on to their morning's tasks.  I headed back upstairs and finally let myself breathe.



I missed staying at the loft, when things were easy and I was free.  I was happy with how things were going with my new recruits, but I was realizing that living with them would mandate changes to my lifestyle.  There were appearances to maintain, and I couldn't be seen slacking off or being a slob.  I couldn't sleep in or put off my shower until later in the day.  I couldn't let myself collapse in a sweaty heap after a hard morning run.  I'd woken up at six in the morning to be sure that I could run, shower, dress and look like I was on top of things by the time they were up.  After a late night, it left me feeling a little worn around the edges.  I harbored some concerns about my ability to help Dinah if this kept up.



The pair had spent some time with their families before returning to my lair.  I'd been anxious in the meantime, worrying they would have second thoughts or turn me in, wearing my costume and waiting in a nearby position in case capes converged on my lair. I'd been both gratified and relieved when they'd returned.  One hurdle crossed.



Both Sierra and Charlotte had seen me bleeding, when I'd come back from rescuing Bryce.  It sounded so minor, but I didn't want them imagining me as hurt and mortal when they were supposed to trust me and look up to me.  What bugged me even more than that was the fact that Charlotte knew my secret identity. I was fairly certain she would keep it to herself, but she'd seen me as \emph{Taylor}.  She'd seen me at what was perhaps the lowest point in my life.  From a distance, but she'd seen it.



Charlotte now served under me out of a mixture of obligation and fear, but I wouldn't feel secure in my reputation until I'd divorced Skitter from that image of a weaker, abused Taylor.



I worked on all five costumes at the same time.  Low-level multitasking was either a minor benefit that had come with my powers or, more likely, a skill I'd developed in the half-year I'd spent micromanaging thousands or tens of thousands of bugs at the same time.  I didn't need to expend any focus on the simple task of laying out the thread, and the only time I really had to pause to give them direction was when it came to the creative input and the more complicated tasks of deciding how everything fit together.  I could only make some calls on style and what would suit the respective recipients' tastes when I'd made enough progress and seen the groundwork laid out.  Where I could, I used my bugs to model ideas and options, forming possible shapes for masks, collars and armor panels.



When I wasn't occupied with that, I focused on Sierra and Charlotte.  I checked their surroundings, discreetly screened nearby groups of people for weapons.  I marked each door with symbols to count the people inside, notified the girls if people were armed, and I put a circle on doors that they were to visit, an `x' on doors they should skip.



A lot of people were ignoring the knocks.  I let them be.  After a few days, if they were still ignoring my minion's attempts to talk to them, I'd maybe give them a bit of a nudge or leave them a message using my bugs.



Apparently overwhelmed with the requests from his various rulers of the Brockton Bay territories, Coil had started delegating some of his people to act as intermediaries.  I got in contact with Mrs. Cranston, the intermediary he'd designated to me, and outlined what I needed.  Waste removal was a big priority, as was clearing out the storm drains so the water could drain from the flooded streets.  I let her know that my services were available if she wanted help identifying where the blockages were, or if the trash removal teams needed protection from interference.



Once those big issues were resolved, a lot of the smaller ones could be attended to.  Too many problems came with large numbers of people spending the majority of their time wading ankle-deep in water that was swimming with warm garbage.



Time passed quickly, what with my focusing on the costumes, Sierra and Charlotte, arranging the cleaning up of the area, using bugs to sweep for troublemakers in my vicinity and experimenting on a smaller scale with dyes and costume options.  I had a smaller collection of Darwin's bark spiders that Coil had procured for me in a specialized terrarium to emulate the hot temperatures they were used to, but I couldn't use them to make anything until they had given birth to at least one new generation.  When I did, though, I expected that the fabric they created would be as superior to the black widow's work as the black widow's silk was to conventional cloth.  There wasn't much room for error with the small number Coil had provided, so I was being careful with the breeding process.



My cell phone rang, and I knew from the bugs I had placed on the two girls that it was Charlotte calling.  That, or someone else had coincidentally phoned me the same instant Charlotte dialed on her phone and raised it to her ear.



``Yes, Charlotte?'' I asked.



``Um,'' she was taken back a little.  ``There's this place here with two families, and they're in the middle of packing up to leave.  I thought you'd want to know, in case they were gone before we came back at noon to eat and tell you about it.''



``That's fine.  What's the problem?''



``Rats.''



Of course.  The trash would offer a steady diet to vermin, and the flooding would deter many of their natural predators.  The rodent population had exploded, and it could easily be getting to the point where it was interfering with people's daily lives.



``Their neighbors have the same problem?''



``We haven't been able to get any of them to answer the door.''



I searched the area around Charlotte.  Sure enough, there were \emph{hundreds} of rodents lurking in the areas where humans weren't active.  They nested in rafters, walls and piles of rubble.  Some were apparently getting courageous enough to venture into people's living spaces, climbing onto tables and into discarded clothes and beds.



No wonder they wanted to leave.



``Tell them to step outside.  If they hesitate, warn them they might get hurt.  They won't, but it'll make them move.''



``Okay.''



I hung up, then hurried to pull on my costume, donning latex rubber socks before pulling on the leggings.  At the same time, I gathered a swarm near the rat house.  I began a systematic attack against the rodents there.  Bees, wasps, hornets, fire ants, regular ants, mosquitoes, biting flies and spiders gathered and began attacking the rats furthest from the house and began steadily working their way inward.  Some rats fought or ran, but more bugs gathered each second.



I hurried out the door and took my shortcut through the false storm drain to the beach.  Drawing a host of bugs around myself, I headed toward the rat house with long strides.



The compartment of armor at my back buzzed, and I reached back to retrieve my cell phone.  It was Grue:



can I come by?



I quickly replied:



On errand.  Don't come to my place.  Meet me at Bayview and Clover.  Not too far from our old place.



It was only a moment before I got a reply:



got it. am already otw.  close.



So he was already on the way when he called?  I wasn't sure what to think about that.  It suggested it was a social call with the assumption I would be okay with it, which I didn't mind, but that didn't really fit his personality.  More likely there was something that he wanted to discuss with me in person.



The rats died at the hands of my bugs, thoroughly poisoned or envenomed, or even eaten alive by the ones that bit repeatedly and didn't even bother to chew or swallow the flesh.  It wasn't a fast job, as there were hundreds of the rodents and they were surprisingly tenacious. I wanted to be thorough.



It took me eight or so minutes to arrive, with the roundabout route I had to take to get from my lair to the beach and then back over toward the Docks.  A heavy cloud of bugs surrounded the house, and a group of eight people of different ages were clustered on the far side of the street, watching the scene like they were watching their house burn down.  Sierra and Charlotte stood apart from the huddle, a short distance away.



I covered my approach with a cloud of bugs and slow, quiet footsteps.  Nobody noticed me arrive.



``Just a minute or two longer,'' I said.  Charlotte and some of the family members jumped.



``You,'' a man who might have been the patriarch of one of the families pointed at me, ``You did this!''



``Yes,'' I answered him.



``Is this some sort of game to you!?  We were prepared to leave, and you keep us from getting our things?  Add another infestation to the one that's already there!?''



``She's just trying to help!'' Charlotte said, with a tone like she wasn't expecting to be listened to.  I got the impression she'd tried convincing him earlier.  I raised one hand to stop her.  It was better if I handled this myself.



The man drew himself up a fraction, ``No reply, huh?  I'd punch you right here, right now, if I thought you'd give me a fair, no-powers fight.''



Irritated, I told him, ``Count backwards from a hundred.  If you still want to when you're done, I'll give you that fight.''



He set his jaw stubbornly, refusing me the courtesy of a countdown.



Ignoring him, I looked at a young boy in the group.  Eight or nine years old, ``What's your name?''



He looked up at his mother, then at me, ``R.J.''



``R.J.  Can you count to a hundred?''



``Of course,'' he looked offended at the idea that he couldn't.



``Show me.''



``One, two, three\ldots''



Only a small fraction of the rats were left.  The largest mass of them had been herded into a corner by the swarm, and in their panic they had done nearly as much damage to each other as they were doing to the bugs.  Stragglers remained elsewhere, but as good as they were at navigating the nooks and small spaces of the house, the bugs were just as good, organized by my will, and they vastly outnumbered the rodents.



``Thirty-one, thirty-two\ldots''



Before the last of the rats were dead, I began organizing roaches and other sturdier bugs to have them cart the dead rats away.  I filled the corners of the stairs with massed insect bodies, until it was more like a ramp than a set of steps.  I stepped up to the house to open the door and let the swarm start bringing the dead rats outdoors.



``Seventy-seven, seventy-eight, seventy-nine\ldots''



I knew I wouldn't quite have enough time to clear out the entire house of the rat corpses, so I cheated by hauling the rats through the walls, into the unoccupied neighbor's residence and out the kitchen window at the back of that building.  The last of my bugs left the sky around the house.  I timed the arrival of the last few dead rats with the end of R.J.'s countdown.



``So many,'' Charlotte gasped, as she saw the three or four hundred rats held high by the swarm.  Judging by the family's expressions, they hadn't known how many rats they'd had nesting inside their home.



Turning to the dad, I told him, ``Your rat problem is dealt with, and nearly all of the bugs are gone.  Some of my swarm will remain so I can keep an eye out for any future infestations, but you won't see them.  Now, if you still want to swing at me, I'm okay to go a round or two.  No powers.''



His mouth twisted in a scowl, but he didn't move to attack me.



Walking over to Sierra and Charlotte, I quietly asked them, ``Would I be right if I guessed he wasn't the one who asked for help?''



``Yeah,'' Sierra said, ``\emph{She} did.''



Sierra pointed at the woman who was protectively clutching R.J.'s shoulders.



``Is this satisfactory?'' I asked the woman, raising my voice.  ``The dead rats will be cleared out of the area in a few minutes.''



``They're really gone?  They won't come back?''



``They're gone, and they won't come back until someone forces me to move out of this territory.''



``Thank you,'' she said.  She opened her mouth as if she was going to say something else, then stopped.



Well, at least the \emph{mom} thanked me.



``You'll want to sterilize the place.  Rubber gloves, bleach.  Boil or replace every dish, every piece of silverware, toothbrushes, linens and clothes.''



``We don't really have the ability to do all that.  We don't have much money, let alone those things.  Stores aren't exactly open, and we don't have running water or electricity either.''



Geez.  ``What have you been drinking?''



``We have a rain barrel and we have a water collector on the roof that came with the supply kit.''



\emph{That's not good enough for this many people.}  ``Do you have a propane tank?  One should have come with the supply kit.''



``It's nearly empty.  We've been using the propane to cook rice, but we don't have measuring cups, and if we use too much water, it takes too long to cook, and so we're running out of the gas.''



She sounded so tired.  Getting by with eight people in one household and no facilities would be such a chore.  Add the stress of rats getting into the food, tearing at sheets to get material for nests, crawling on them as they slept?  I didn't know how she'd coped.



I hoped my dad's situation was better.



``Make a note,'' I ordered Sierra, ``If these people are having trouble, it's easily possible others are in similar straits.  We'll want a fresh set of supplies going out to everyone in my territory.  For this family, a delivery of cleaning supplies; bleach, rubber gloves.  They'll want some new clothes, you can get their sizes after I leave.  Supplies, of course, and containers to keep the food in.  Tupperware.  We'll arrange for a doctor to come by and check them for bites, scratches and infections.  Standard inoculations.  The doctor will know how to handle that stuff better than we do.''  \emph{Hopefully}.



``Okay.''



``And measuring cups.''  I smiled behind my mask.



``We can't pay you back for this, even if you give us a loan, we won't be able to.'' the mom said.



So they were assuming I was putting myself in some loan shark role.  Get them indebted to me, leech them for cash.



``It's on the house,'' I waved her off.



``Thank you,'' she said, again.  I felt bad for feeling the way I did, but I thought her gratitude was a little muted for what I was giving her.



I could sense Grue a block away, my bugs settling on his helmet, unable to see as they got close.  I could feel that faint push of the darkness billowing away from him.  He'd been watching for a minute or two.



``If there's nothing else that's pressing?'' I asked.



Silence, a few shaken heads.  I turned to go and meet Grue where he stood at the corner of one building.



``Taking up a side business in extermination?'' he asked me.  I thought I detected a note of humor in his voice.



``Assisting my people.  Some goodwill will help when I'm more firmly in power here.''  I couldn't help but sound a mite defensive.



``Yep.  That guy over there will be singing your praises.''



I looked over my shoulder at the `dad' who'd been giving me a hard time.  He was ignoring Sierra and Charlotte, who were talking to the larger group of people.  Instead, he watched the bugs cart the dead rats down the street, as if he thought I would slack on the job.



``I don't understand people sometimes.''



``My guess?  When everything went to hell, he told himself he'd be the `man' for his family.  Take charge, provide, protect.  He failed.  Then some little girl waltzes in and takes care of all that all at once?''



``Little girl?''



``You know what I mean.  Look at it from his perspective.''



``What if I recruited him?  Gave him the opportunity and the power to help others?''



``He'd be intolerable.  I mean, sure, things would get better in the short-term.  But over the long haul? You'd wind up with someone who criticizes every last thing you do, every last call you make, to make himself feel better about the fact that he isn't the one in control, the one calling the shots.''



``Fuck,'' I said.  ``I thought you said you weren't good with people.''



``I'm not good with \emph{girls}, mainly.  Guys?  Or `manly' guys like him?  I've met enough people like him in the gyms with my dad, in fighting classes.''



``Guys and girls aren't that different.''



``Aren't we?  Look at our group.  Regent and I are going on the offensive.  I've got Aisha and I making constant, coordinated attacks against enemies in my territory, terrorizing groups with attacks from the cover of my darkness, or from someone they can't even remember fighting.  Regent's got a squad of Coil's soldiers with him, and he's tracking and kidnapping the leaders of enemy groups and gangs, using his power to control them and then having them sabotage their own operations, or start fights with other groups that leave both almost totally wiped out.  Then he cleans up the mess.''



``And us girls?''



``Lisa's running the shelter, and she says she's doing it to get more info, but I think she doesn't mind how it connects her to the community there, either.  You, too, are almost nurturing in how you're treating the people in your territory.  And you're acting like you're getting that aspiring superhero thing out of your system.  Or entrenched deeper into it.  I can't tell.''



I didn't like that he was mentioning that.  Sore spot for both of us.  ``Just following my instincts.''



``And maybe pushing yourself a little too hard, too fast in the process.''



``Mmm,'' I offered a noncommittal response.  I could have asked how Bitch fit into his interpretation of events, but I already knew the answer.  Normal rules didn't apply to her.  ``I think all this ties more closely into how our individual powers work than it does to gender.''



``Maybe.  But\ldots no,'' he changed his mind after thinking for a second.  ``I think both you and Lisa could be a \emph{lot} more aggressive.  It kind of worries me that you aren't.''



``Worries you?''



``If you aren't taking out the other gangs in your territory and turning a profit, why should Coil bother keeping you there?''



``First of all, I'm totally prepared to squash any troublemakers the second they make themselves known around here.''



``Assuming you can find them.''



``I can.  \emph{Second of all, }Coil didn't say a thing about turning a profit.  He has money.  Scads.''



``He has his \emph{own} money.  Money that he has to devote time and attention to earning.  If your territory never starts earning for him and just becomes some black hole that sucks up tens of thousands of dollars of his money each week, you think he's going to be okay with that?''



``What do you want me to do?  That doesn't involve taking protection money or peddling drugs?''



``Those would be your biggest revenue streams.''



``I'm taking control like he wanted me to.  Faster than the rest of you.''



``But you're not leaving yourself in a position to \emph{do} anything with that control.''



``I can get all of the people in my territory onto Coil's side.  And I have over three hundred and fifty thousand dollars I can put towards infrastructure here.''



``That's not as much as you might think it is, when you're talking about this much territory.''



``No, but it's \emph{something}.  Look, Coil's a proud guy.  He said it himself.  He'd be upset if he took over the city and it wasn't better than it was before.  I've got the old Boardwalk here.  I can help set that going again.  I've also got the Docks, here.  A part of it.  If I can improve things here, if I can take this place and make it better than it's been in decades, wouldn't that be a feather in his cap?''



``Even if things went smoothly, that's not going to happen fast, and it's not going to be easy.''



Not fast.  Grue had been pretty merciless in trying to poke holes in my approach, but the realization that he was right on that score was like a punch in the gut.  ``If I can show Coil I'm making headway\ldots''



Even I wasn't convincing myself.  Coil wouldn't give Dinah up for something as minor as a good \emph{start}.  I think Grue noticed my dejection.



``I'm sorry if I'm being hard on you,'' Grue settled one hand on the armor of my shoulder.



``No.  You're right.  I've been thinking too short-term.''



``I really did want to come by and talk about less serious things.  It's a shame we can't.''



``We have time to do that, don't we?  We could go back to my lair, hang.  I can show you what I've got done on your new costume, and we could talk about the mask,'' I suggested.



He shook his head.  ``No.  What I meant was that I'd hoped to spend \emph{today} talking about that stuff.  But we're not going to get the chance.  Something more serious has come up.''



``Oh hell.''  My initial suspicions had been right.  This wasn't a social call.



``Regent got a visit from one of the Slaughterhouse Nine last night.  So did Coil, though the man is quiet on details.  Coil's also reporting that Hookwolf got a visit on Tuesday, and one of Coil's undercover operatives died in the ensuing carnage.  The PRT office downtown \emph{also} got hit, according to Tattletale\ldots''



``They're active.''



``Yeah.  More to the point, they're \emph{recruiting}.  Looking for a ninth to round out their group.  Regent was one candidate.''



``Who was the other, at Coil's?''



``Coil isn't saying.  We think, with Tattletale's educated guess helping us out, that Hookwolf might have been another possible recruit.''



``And at the PRT offices?  Shadow Stalker?''



``As good a guess as any.  We're not sure where she wound up.''



``So what does this mean?''



``It means Hookwolf is calling together a meeting of the local powers that be.  Crook, criminal, mercenary and warlord.  We have to decide if we want to go.''



``He was one of the people they visited.''



``He was.  Which means this could be a trap.  Some kind of grand slaughter to commemorate his joining the group.  Taking out the other prospective members in the process, like Regent.''



``Or it could be a target for the Slaughterhouse Nine to attack.  Create chaos, maximum bloodshed, the kind of stuff that gets attention.  They'd be killing some of their possible recruits, but that'd suit them, being unpredictable, never letting you think you're safe.''



Grue nodded.



``At the same time, if we \emph{don't} go, it's crucial info that we're missing out on.'' I thought aloud.  ``What does Dinah say?''



``Her power is out of commission after the attack on Coil's base, apparently.''



``So we're flying blind, with only Coil's power to back us up.''



``Whatever it is.''



``Whatever it is.'' I echoed him, feeling bad for the dishonesty and my lack of disclosure. ``What do Coil and Tattletale have to say about the meeting?''



``Coil wants everyone present.  Tattletale thinks Hookwolf is on the up and up, but he's only one of the potential problems that could come up.''



I thought of the others who would be at the meeting.  ``Like the fact that Skidmark is one of the local powers.  Or he is if he's managed to recuperate rep-wise from the ass kicking that Faultline gave him.  He's not exactly the type to keep to the truce at the meeting.  An unpredictable element.''



``Yeah.''



``But if Tattletale is right, and Hookwolf isn't on the side of the Slaughterhouse Nine, if we can trust Skidmark to have the basic common sense to back the rest of us up if they attack--''



Brian turned toward me, and I could imagine him giving me an `are you serious?' look behind his visor.



``--Or at least not get in our way,'' I corrected myself.  ``We could fight back, if it wound up being most of the villain groups against the Nine.  Our group's powersets lend themselves to slipping away if that went sour, and Tattletale might be able to sense trouble before it hit us.''



``You're talking like you want to do this.''



``I do.  Kind of.  If all the top villains of the city attend and we don't, are we really doing ourselves any favors?  Our rep will take a nosedive, we'll be out of the loop, and there's nothing saying we wouldn't be targeted by the Nine all the same if we sit it out.''



``Why do I get the feeling your decision here is motivated by your rushed attempts to get more control, more rep and finish this phase of our territory grab as soon as possible?''



``Because it is.''



He sighed, and the sound was eerie, altered by his darkness.  ``To think I used to \emph{like} that you were hardcore serious about the supervillain thing.''



That touched on that sensitive subject again.  My original motivations, my act, such as it was back then.  I turned the subject of our debate back to the meeting.  ``What do you think?  If it was up to you and you alone, would you want us to go?''



``No.  But it \emph{isn't }up to me and me alone.  When I weigh everything in my head, including the risk of our groups spending time fighting and arguing on the subject when we could be organizing and putting measures in place to protect our territory in our absence?  I think it makes more sense to accept it and go with the flow.''



``When is the meeting?''



``With a situation this critical?  There's no time to waste.  Tonight.''





