





I'd spent nearly sixteen years in Brockton Bay, living a half-hour's walk away from the ocean and I couldn't remember ever being on a boat.  How sad was that?



I mean, I was sure I'd been on a boat before.  My parents had to have taken me on the ferry when I was a baby or toddler.  I just didn't remember any of it.  My parents were introverts, by and large, and their idea of an outing had been more along the lines of a trip down the Boardwalk, a visit to the Market or going to an art gallery or museum.  Maybe once in a while we'd go to something more thrilling like a fair or baseball game, but no\ldots this was the first time I could remember being out on the water.



It was exhilarating, the boat ride.  I was surprised by how much I enjoyed it.  I loved the feeling of the wind in my hair, the slight turbulence as the boat bounced on the short waves.  It wasn't that different from how I had enjoyed riding Bitch's dogs, and there was none of that primal, deep-seated worry that the hulking monster I was riding would turn around and snap my face off.  I'd almost think I had been destined to fly, based on how thoroughly I enjoyed myself, and that it was only bad luck that I'd gotten other powers instead\ldots except I remembered flying with Laserdream as the Endbringer attacked, and  that hadn't been the most enjoyable experience.  That might have been a special circumstance; I'd been dealing with the fact that I'd had a broken arm, I'd recently puked my guts out, I'd been soaking wet, and an \emph{Endbringer} had been working on wiping my hometown and everyone I cared about from the face of the planet.



That day would almost feel like something that had happened in a dream, if I hadn't spent every hour of every day since living in the aftermath.



Coil's people had dropped us off along with two sleek motorboats, depositing them at the water's edge.  Grue was in one boat with Bitch, her three dogs and a puppy she had on a long chain.



I wasn't sure if the puppy conveyed the image we wanted, but with her attitude towards me lately, I wasn't willing to comment and risk her going off on me.  She'd remained angry after I'd called her out on her screwing me over and setting me up for Dragon to arrest, but she'd left me more or less alone.



The puppy \emph{was} cute.  It was skittish, especially around people, which seemed a little odd.  It wasn't the kind of dog I'd expect Bitch to favor.  Too young, not vicious or intimidating in appearance.  On the other hand, skittish as it was, it had an aggressive streak.  It constantly hounded Bentley, nipping at his flanks, then spooking and running away the second the bulldog looked at him.  It had made for a fair amount of noise when we'd been getting the boats into the water.  One for Bitch, her dogs and Grue, one for the rest of our group.



Our boats weren't out on the ocean.  We traveled through the area downtown where Leviathan had collapsed a section of the city.  It was now more or less an artificial lake.  The water was fairly still, lapping gently against the ruined roads and collapsed buildings that surrounded the crater, but with the speed these boats were capable of going, even waves a half-foot high made us ramp slightly off one and then crash down onto the next with a sudden spray.



Tattletale was at the back, steering the thing.  It seemed counter-intuitive, with the boat going the opposite direction she pushed or pulled the stick.  Still, she seemed competent at it.  Better than Grue, which I found slightly amusing.



From time to time, I was finding myself in a strange emotional state.  As I stayed alert for it, I was able to catch those moments, try to pick them apart for what they were.  The high-end motor whirred and the boat bounced over the waves, the wind and water getting in my hair, all while we headed into the most ridiculously dangerous and unpredictable situation we'd been in for weeks. It was one of those moments; I felt almost calm.



For a year and a half, I'd spent almost all of my time in a state of constant anxiety.  Anxiety about schoolwork, my teachers, my peers, my dad, my mom's death, my body, my clothes, trying to hold conversations without embarrassing myself, and about the bullies and what they would do next.  Everything had been tainted by the constant worries and the fact that I'd constantly been preparing for the worst case scenarios and maybe even setting up self-fulfilling prophecies in the process.  I'd spent every waking moment immersed in it.  Either I was stressing over something I'd done or something that had happened, I was concerned with the \emph{now}, or I was anxious over what came in the future: distant or near.  There was always \emph{something}.



And that was \emph{before} I'd ever put on a costume and found myself caught up in my double-crossing plan against the Undersiders and everything that had stemmed from that.  Before Dinah and running away from home, before I'd decided to go villain.  Stuff that made some of what I'd been worried over before seem trivial.



So why could I feel calm now?



I think it was that realization that there were moments where I was helpless to act, oddly enough.  This boat?  Speeding across the Endbringer-made lake?  I had to be here.  There was no other option, really.  As I clutched the metal rim of the boat with one hand while we soared forward, the wind in my hair, I could accept the fact that I couldn't do anything in this time and place to get Dinah out of captivity sooner.



With that in mind, I surrendered myself of that responsibility for the present.  Much in that same way, I cast off all the other worries, great and small.



A light flashed ahead of us.  Three blinks, then two.



``Regent!'' Tattletale called out.



Regent raised a flashlight and flashed it twice, paused, then flashed it twice again.



There was one flash in response.



Grue slowed his boat as we reached our destination.  Our meeting place was in the center of the lake, one of the buildings that still partially stood above water, leaning to one side so a corner of the roof was submerged, the opposite corner peaking high.  Tattletale didn't slow our boat like Grue had his, and instead steered the boat in a wide `u' to ride it up onto the corner of the roof.  Regent and I hopped out to grab the front of the boat and help pull it up.  When Grue rode his boat aground as well, a little more carefully, we helped him too.  Bitch hopped out and spent a moment using gestures and tugs on the puppy's leash to get her dogs arranged and settled.



Hookwolf and his Chosen had situated themselves at the corner of the roof that stood highest from the surrounding water.  Hookwolf stood with his arms folded, densely covered in bristling spikes, barbs, blades and hooks, only his face untouched by the treatment, covered by his metal wolf mask instead.  Othala, Victor and Cricket were sitting on the raised edge of the roof behind him.  Stormtiger floated in the air just beside Cricket, and Rune had levitated three chunks of pavement into the air behind the group, each the size of a fire truck, like weapons poised at the ready.  She sat on the edge of one of the chunks, her feet dangling over Victor's head.  Menja stood just behind Rune on the floating piece of shattered road, twelve feet tall, fully garbed in her valkyrie armor, a shield in one hand and a long spear in the other.



I almost missed it in the gloom, but when I did spot it, it was almost impossible to ignore.  On every patch of skin I could see in the Chosen's group, scars and scratches had just barely healed over.  There were still faint indents and lines of pale skin that marked where the deep lacerations had been.  The little scars made patterns across their skin, some spraying out from a single point, others running parallel to one another, going in the same direction like a snapshot of rainfall imprinted on their skin.  With that many scratches and scars, they must have been hit hard.



Faultline's group was gathered to one side.  Faultline, Newter, and the new member Shamrock wore more concealing costumes than their usual.  Faultline's face was covered in a tinted visor, and her arms and legs were covered in opaque gloves and leggings.  Labyrinth and Spitfire were fully decked out in their usual concealing robe and fire-retardant suits, respectively.  Only Gregor showed skin.  The barnacle-like growths of spiral shells that covered his skin had multiplied on one side of his body, until there was more shell than skin.  The skin around it was crimson enough that it stood out in the gloom.  It looked tender.



I saw a flash of light above us, and spotted Purity in the air high above the rooftop, using her power to create a flare of light, extinguish it, then create it again.  There was an answering series of flashes from across the water.  It was a different set of signals than the ones she'd set up with us.  It made sense for the light signals to be different from group to group, so Purity could keep track of who was coming and where from.  The main reason we'd agreed on this meeting place were the seclusion it offered, and the fact that it was just hard enough to access that the Nine wouldn't be able to approach without us knowing.  Hopefully.



All at once, an incoming boat made its presence known.  As though a switch was flipped, there was the sound of something that sounded like the combined noise of radio static coming from a bank of speakers, an eighteen wheeler with the muffler off and an onrushing train.  It wasn't just noise – the vehicle flickered with flashes of electricity and lights that people could probably see from anywhere downtown.



Seeing it approach, I had no doubt it was a tinker contraption.  It was the size of a small yacht, but it looked outfitted for war, with what looked like tesla coils crossed with old school tv antennae fueling its forward momentum and sending arcs of electricity dancing over the waves in its wake, as though it was riding on a current of lightning.  Various guns had been placed haphazardly around the upper deck, each manned by a Merchant.  Skidmark stood at the highest deck with Squealer, the driver.



Squealer had apparently never grasped the concept of \emph{elegance} in design.  From what I'd read and heard, she went for size, augmentations and additions when she built her vehicles.  She was kind of the polar opposite of Armsmaster in that regard.



The hull of their boat scraped against the edge of the building, nearly running over the boat that Grue and Bitch had come in on.  All of the lights shut off, and the Merchants descended onto the roof.  Skidmark, Squealer, Mush, Scrub, Trainwreck, the telekinetic whirlwind lady with the long hair and one other.



Another reason for this meeting place had been subtlety, keeping out of sight and off the radar.  The Merchants apparently hadn't gotten the message.



``Hey!'' Hookwolf growled, ``What part of keep a low profile don't you fucking understand?''



Skidmark smirked, raising his chin to give it an arrogant tilt, ``We did.  My Squealer built a box that cancels out light and noise at a certain distance.  Nice and in your face up close, almost invisible and silent when far away.  Isn't that right, baby?''



Squealer just smiled.  It probably wasn't as sexy or cute as she thought it was.  Aisha, when left to her own devices, was a pretty girl who dressed trashy.  Squealer, I felt, was more of a trashy woman who dressed trashy.



``Hey, Faultline,'' Skidmark's smirk dropped off his face as he realized who else was present.  ``What the motherfuck were you doing, fucking with my party!?''



``You had something we needed.''  Faultline's response was as measured and calm as Skidmark's question wasn't.



``Who hired you, bitch?  Tell me and my Merchants won't come after you in revenge.  All you'll have to do is return that shit you stole or pay me back for it.  Maybe you can spit-polish my knob for a little goodwill.''



``Not going to happen.''



``Then forget sucking my cock.  Pay me back and tell me who hired you and we'll call it even.''



She shook her head.  It was more the kind of head shake that accompanied an eye roll.



Skidmark went on, ``You're mercenaries.  Don't tell me you don't have the cash.  I'll only ask for five mil.  One for each vial you took.''



Fautline didn't answer him.  Instead she looked at Hookwolf and asked him, ``Did we really need to invite him?  Does he contribute \emph{anything} to this discussion?''



``He has nine powers on his team,'' Hookwolf responded.  ``Ideology isn't important.''



``He doesn't \emph{have} an ideology.  He's just an idiot.''



``Enough of that,'' Hookwolf snarled, his voice hard with a sudden anger.  ``We don't fight amongst ourselves.  Not on neutral ground.  Both of you shut the fuck up.''



Faultline shook her head and leaned over to whisper something to Shamrock.  The Merchants settled themselves on the side of the roof opposite our group.  Skidmark gave Grue the evil eye.  Was he still resentful over what had happened at the last meeting?  Being denied a seat at the table?



Another series of flashes served to alert us, indirectly, of incoming arrivals.  The Travelers appeared soon after.  Trickster, Sundancer, Ballistic each stood on the back of some kind of turtle serpent.  I couldn't make out Genesis's form in the gloom.  What little light was available came from the moon and Purity's radiance from where she floated above us.  I could have used my bugs to get a feel for the shape Genesis had taken, but my habit was generally to place my bugs on clothing where they wouldn't be noticed, and Genesis was effectively naked.  I didn't know anything about them, but they were our allies.  I didn't want to irritate her and upset anything between our two groups.



Coil was the last of us to arrive, maybe because he'd wanted to be fashionably late.  The two soldiers who'd driven his boat stayed behind.  Purity set down by where the boats had landed, followed by Fog and Crusader, who I hadn't seen in the dark.  Night stepped out of the lake, between our parked boats and onto the roof, water streaming from her cloak.  Had she been the just-in-case measure if an incoming boat hadn't known the signal?  She would be invisible in the pitch black gloom beneath the water's surface, which would mean she wasn't in her human form.



The way the Travelers and Coil had positioned themselves, we'd formed a haphazard ring.  From the top of the roof, going clockwise, the arranged groups were Hookwolf's Chosen, Faultline's crew, us, the Pure, Coil, the Travelers and the Merchants.



``It seems everyone is here,'' Coil spoke, taking in the collected villains.  Forty-ish of us in all.



``Not quite everyone,'' Hookwolf replied.  ``Victor, Othala.''



Othala touched Victor, and Victor raised one hand.  A fireball appeared in it, then disappeared as he clenched his hand.  He repeated the process two more times.



``Who are you signalling?'' Purity's asked.  Her hand flared with light, ready to fire.



``It would be a grave and stupid mistake if you invited the Nine,'' Coil told Hookwolf.



``We're not stupid,'' Hookwolf said.  Three answering flashes appeared over the water.  I heard the faint noise of a boat motor.  Everyone present on the roof readied for a fight, turning towards either Hookwolf or the incoming boat.  I used my power to call on local crabs, and to draw out the bugs I'd stored in the boat, keeping them close to me.



There were three more flashes, close, and Victor responded again.  In moments, the boat arrived.  It wasn't the Nine.  It was the good guys.



Miss Militia was first out of the boat, and Battery activated her power to haul the boat up onto `land' in a flash before stepping up to Miss Militia's side.  Triumph, Weld and Clockblocker rounded out their group.  Our circle made room, though half the people present seemed to be tensed and ready to use their powers with the slightest excuse.



``It seems we have a problem,'' Miss Militia spoke, as her group took her place between the Pure and us Undersiders.



``We do,'' Hookwolf said.  ``Two problems, actually.''



``Two?'' Purity asked.



Hookwolf pointed at the Travelers, then pointed at Grue and the rest of our group.  ``They're being cocky, think they're being clever.  Figure we should get all this out in the open, at least so you're aware.  You too, Coil, Miss Militia.''



``Perhaps you'd better explain,'' Coil responded.



Hookwolf pointed at each of us in turn, ``Grue has been making attacks against my people in the upper downtown area.  Howling has been heard in the Trainyard.  Bitch.  Regent was sighted in the college neighborhoods.  Skitter made a move to take over the Boardwalk and claim it for herself.  Tattletale is either abstaining, or more likely, putting herself in the middle of the Docks and keeping her head down.''



``So?'' Tattletale asked.



Hookwolf ignored her.  ``Downtown we've got Ballistic attacking my people in the upper downtown neighborhoods, north of this lake here.  Sundancer was spotted in the shopping district, Genesis at the downtown coast, near the south ferry station. Trickster has been driving looters out of the heart of downtown, the towers.  You seeing the pattern?  All of them alone.  Most of them making moves to take a piece of the city for themselves.''



``We already knew they were talking territory,'' Miss Militia responded, ``This isn't a priority.  The Nine-''



``They haven't taken territory,'' Hookwolf snapped back, ``They're taking the \emph{city}.  Split it up all nice and proper between them, and now they're taking advantage of the distraction the Nine are giving them to secure their positions before we fucking catch on.''



Grue looked at Trickster, and there was some kind of unspoken agreement between them.  Knowing Grue, I was certain he was deliberately ignoring Coil.  No use volunteering more information than necessary.



Trickster spoke, ``We didn't know the Nine were around before we put this into motion.''



There was a flicker of surprise on Purity's face.  ``So Hookwolf is right.  You \emph{are} taking over.''



``Something like that,'' Grue responded.



What was Hookwolf's game?  Had he brought everyone here under a different pretext so he could ambush us on this front?



``This isn't of any concern to us,'' Miss Militia spoke, stern.  ``The only reason we're here is to get information on the Slaughterhouse Nine, their motives, and strategies for responding.''



``That might help you in the next week or two, but a month from now you'll be regretting it,'' Hookwolf told her.



``Quite frankly, I don't think we have any other choice,'' Miss Militia replied.



``We do,'' Hookwolf said.  ``They want us to lose our territories to them while we busy ourselves dealing with the Nine-''



``That's \emph{not} our intent,'' Trickster cut him off.



``Pigshit,'' Skidmark muttered.  He looked angry.  Even Purity had a hard cast to her face, or what I could see of it through the glare of her eyes and hair.  These were people who thought highly of themselves.  Whether that self-esteem was deserved or not, they didn't like being played for fools.



All at once, this meeting had become about \emph{us} versus \emph{them}.  The Travelers and the Undersiders against everyone else.



Hookwolf said, ``Then agree to a truce.  So long as the Nine are here, you're hands off your territories, no fighting, no business.  We can arrange something, maybe you all stay at a nice hotel on the Protectorate's tab until this is dealt with.  That'll mean we can all focus on the \emph{real} threat.''



Stay in a hotel until the Nine were dead, arrested or driven out of town.  He couldn't seriously expect us to do that.



``I'm inclined to agree,'' Coil answered, after a moment's consideration.  ``Perhaps now is an opportune time to share this information:  I have sources that inform me that should Jack Slash survive his visit to Brockton Bay, it bodes ill for everyone.''



``That's vague,'' Faultline spoke.



``I'll be more specific.  Should Jack Slash not die before he leaves Brockton Bay, it is very likely the world will end in a matter of years,'' Coil spoke.



``Bullshit,'' Skidmark answered.  The others were showing varying reactions.  I doubt many bought it.



``You contacted us to say something very similar a couple of days ago.'' Miss Militia said, ``But I have the same questions now that I did then.  Do you have sources?  Can you verify this?  Or provide more information?''



Behind her, Weld reached into his pocket and withdrew his smartphone.



``More information?  Yes.  I have sought further details and pieced together a general picture of things.  Jack Slash is the catalyst for this event, not the cause.  At some point in the coming years, Jack Slash kills, talks to, meets or influences someone.  This causes a chain of events to occur, leading to the deaths of anywhere from thirty-three to ninety-six percent of the world's population.''



That gave everyone pause.



Coil went on, ``If Jack Slash is killed, the event is likely to occur at some point in the more distant future instead.''



``Dinah Alcott,'' Weld spoke.  All eyes turned to the metal-skinned boy.



``Beg pardon?'' Coil asked.



``Thursday, April fourteenth of this year, Dinah Alcott was kidnapped from her home and has not been seen since.  Dinah had missed several weeks of classes with crippling headaches in the months before her disappearance.  Investigation found no clear medical causes.  Police interviewed her friends.  She had confided to them that she thought she could see the future, but doing so hurt her.''



``You think Dinah is Coil's source.  That makes a lot of sense.''  Miss Militia turned from Weld to Coil, and her voice was heavy with accusation, ``\emph{Coil}?''



``I did not kidnap her.  I offered Dinah training and relief from the drawbacks of her abilities on the contingency that she immediately cut off all contact with her family and friends and provide me a year of service.''



He lied so smoothly, flawlessly.  What really rattled me was hearing him refer to her as Dinah for the first time.  Coil added, ``She took a week to decide, then contacted me during one of her attacks.''



Of course, the heroes weren't about to take his word for gospel.  Miss Militia's lips pursed into a thin line.  ``Could I contact her to verify this?''



``No.  For one thing, I have no reason to let you.  Also, the process of gaining control of her power requires that she be kept strictly isolated from outside elements.  A simple phone call would set her back weeks.''



``So Coil has a precog,'' Hookwolf growled, ``That explains how he always seemed to fucking get the upper hand when he pit his mercenaries against the Empire.''



Coil clasped his hands in front of him, ``I knew you might come to these conclusions if I volunteered this information.  You all should already know I am not a stupid man.  Would I weaken my position if I did not wholeheartedly believe that what I was saying was correct?  \emph{Jack Slash must die, or we all die.}''



``And to maximize our chances for this to happen,'' Hookwolf added, ``The alliance of the Travelers and the Undersiders must concede to our terms.  They hold no territory until the Nine are dead.''



Coil deliberated for a few seconds.  ``I think this makes the most sense.''



Skidmark and Purity nodded as well.



Coil's response caught me off guard.  He was throwing us to the wolves to maintain his anonymity in things.  I felt my heart sink.



It made sense, on a basic level, and I could see why the other groups were agreeing.  I mean, our territory wasn't worth risking that the world ending.  Coil was apparently willing to delay his plans, or \emph{pretend }to delay his plans while he carried them out in secret.  But I would be giving up my territory, condemning Dinah to more days, more weeks of captivity.



I \emph{really} didn't like that idea.



``Easy decision for you guys to make,'' Trickster said, chuckling wryly, ``You're not giving anything up.  In fact, if we went with your plan, there'd be nothing stopping you from sneaking a little territory, passing on word to your underlings to prey on our people, consolidating your forces and preparing them for war, all while we're cooped up in that hotel or wherever.''



He was right.  I could imagine it.  Not just weeks, but \emph{months} lost.  We'd just lost the element of surprise thanks to Hookwolf outing us here, and the local villains and heroes were now all too aware of the scale of what we were doing.  Add the fact that they would get a breather?  A chance to regroup and prepare?  To retaliate?  Regaining any of the ground we lost while we helped hunt down the Slaughterhouse Nine would be excruciating.



In those weeks or months it took to retake territory and slog ahead with constant opposition, there could be further delays.  It would mean that my plan to efficiently seize the Boardwalk and surrounding Docks would fall apart.  I'd have to pull away from my people and my neighborhoods to help the others fight off attacks.  I wouldn't be able to offer exemplary service to earn Coil's trust and respect in the mess that ensued.  The opportunity to free Dinah would slip from my grasp.



Worst of all, there was no reason for it.  We'd claimed more of the city as our territory than they had assumed, and now Hookwolf was building on that, giving them reason to worry we had \emph{other} sinister motives.



``No,'' I murmured, barely audible to myself.  I could see some of the other Undersiders -Grue, Tattletale and Bitch- turn their heads a fraction in my direction.



``No,'' Grue echoed me, his voice carrying across the rooftop.



``\emph{No?}'' Coil asked, his voice sharp with surprise.  Was there condemnation in there?  It was  very possible we weren't going the route he wanted.



Grue shook his head, ``We'll help against the Nine.  That's fine, sensible.  But Trickster is right.  If we abandoned our territories in the meantime, we'd be putting ourselves in an ugly situation.  That's ridiculous and unnecessary.''



Trickster nodded at his words.



``If you \emph{keep} them you'll be putting yourself in an \emph{advantageous} position,'' Purity intoned.



``Don't be \emph{stupid}, Undersiders, Travelers.'' Faultline cut in, ``You can't put money, power and control at a higher priority than our collective survival.  If Coil's precog is right, we have to band together against the Nine the same way we would against an Endbringer.  For the same reasons.''



``And we \emph{will},'' Trickster said.  ``We just won't give up our territory to do it.''



``Because you're hoping to expand further and faster while the Nine occupy the rest of us,'' Hookwolf growled. ``We agree to this like you want, and you attack us from behind.''



``We haven't given you any reason to think we'll betray a truce,'' Grue told him, his voice echoing more than usual, edged with anger.  The darkness around him was roiling.



``You have.  You're refusing the terms,'' Purity said.



Hookwolf was manipulating this.  He wasn't as subtle about it as Kaiser had been, it was even \emph{transparent,} what he was doing.  Dead obvious.  At the same time, the scenario he was suggesting was just dangerous and believable enough to the Merchants, to his Chosen, and to the Pure that they couldn't afford to ignore it.  Coil couldn't talk sense into them without potentially revealing his role as our backer.  Even the heroes couldn't counter his argument, because there was that dim possibility that he was right, that they would lose control of the city to villains if we continued to grab power.



Which was admittedly the case.  Dealing with the local heroes was one of our long-term goals, for Coil's plan.



We were fighting for Coil's plan and Coil wasn't helping.  He remained silent, inscrutable, sticking to the situation that worked best for him and him alone.  Damn him.



``You'll be earning the enmity of everyone here if you refuse,'' Hookwolf said.  Was there a hint of gloating in his tone?



``We'll be ruining ourselves if we agree, too,'' Grue retorted.



``I strongly recommend you agree to this deal,'' Purity said.



``No, I don't think we will,'' Trickster said.



``No,'' Grue echoed Trickster, folding his arms.



That only provoked more argument, along many of the same lines.  It was clear this was getting nowhere.



I turned to Miss Militia, who stood only a few feet from me.  When I spoke to her, she seemed to only partially pay attention to me, as she kept an eye on the ongoing debate.  ``This isn't what we need right now.  Hookwolf's made this about territory, not the Nine, and we can't back down without-''  I stopped as she turned her head, stepped a little closer and tried again, ``We, or at least \emph{I} have people depending on me.  I can't let Hookwolf prey on them.  We all need to work together to fight the Nine.  Can't you do something?''



Miss Militia frowned.



``Please.''



She turned away from me and called out, ``I would suggest a compromise.''



The arguing stopped, and all eyes turned to her.



``The Undersiders and Travelers would move into neutral territory until the Nine were dealt with.  But so would the powered individuals of the Merchants, the Chosen, the Pure, Coil and Faultine's Crew.''



``Where would this be?  In the PRT headquarters?'' Hookwolf asked.



``Perhaps.''



``You were attacked as well, weren't you?  Who did they go after?''



``Mannequin went after Armsmaster.  Armsmaster was hospitalized.''



That was some small shock to everyone present, though I might have been less surprised than some.  Armsmaster as a prospective member for the Nine.



``What you suggest is too dangerous,'' Faultline said.  ``We'd all be gathered in one or two locations for them to attack, and if Armsmaster was attacked, we could be too.''



``And their whole reason for being here is recruitment,'' Coil spoke, ``Perhaps the plan would work if we could trust one another, but we cannot, when many here were scouted for their group, and may turn on their potential rivals to prove their worth.  We would be vulnerable to an attack from within, and we would be easy targets.''



``We could make the same arguments about ourselves,'' Grue pointed out, ``If we agreed, we'd be sitting ducks for whoever came after us.''



``I think the Protectorate can help watch and guard \emph{nine} people,'' Coil replied, ``I'm less confident of their ability to protect everyone present.''



So Coil wasn't willing to play along if it meant losing his ability to stay where he was, but he \emph{was} willing to make life harder on us, his territory holders.  Did he have some plan in mind?  Or was he just that callous?  Either way, he was an asshole.



``No.  I'm afraid that \emph{compromise} won't work,'' Hookwolf said, squaring his shoulders.



Miss Militia glanced my way.  She didn't say or do anything, but I could almost read her mind: \emph{I tried}.



Hookwolf wasn't about to give up anything here.  He had us right where he wanted us, and he was poised to kill two birds with one stone: The Nine and his rivals for territory.



``It seems,'' Hookwolf said, ``The Travelers and the Undersiders won't agree to our terms for the truce.  Merchants, Pure, Faultline, Coil?  Are you willing to band together with my group?''



Purity, Coil and Skidmark nodded.  Faultline shook her head.



``You're saying no, Faultline?''



``We're mercenaries.  We can't take a job without pay.  Even a job as important as this.''



``I will handle your payment here as I did for the ABB, Faultline,'' Coil said, sounding just a touch exasperated.



``And Miss Militia?'' Hookwolf asked, ``A truce?''



``Keep the business to a minimum, no assaulting or attacking civilians,'' Miss Militia said, ``We still have to protect this city, there's no give there.  Don't give us a reason to bother with you, and we'll be focused wholly on the Slaughterhouse Nine in the meantime.''



``Good.  That's all we ask.''



The leaders of the new group crossed the roof to shake hands.  In the process, things shuffled so that our group, the Travelers and the heroes were near the bottom of the roof.  The heroes moved off to one side, as if to guard us from any retaliation, making the separation in forces all the more obvious.



``You guys are making a mistake,'' Grue said.



``I think you have things the wrong way around,'' Hookwolf said.  ``Nobody wants to break the peace at neutral ground, so perhaps you should go before things get violent?''



Tattletale asked, ``You won't let us stick around and discuss the Nine, who they attacked, what our overall strategies should be?  Even if we aren't working together as a single group?''  She paused, looking deliberately at Faultline, ``You know, the \emph{smart} thing to do?''



She was met only with cold stares and crossed arms.



There was little else to be said or done.  We'd lost here.  I turned and helped push our boat into the water, then held it steady as everyone piled in.  Tattletale had started the motor, and we were gone the second I'd hopped inside.





