





``Fuck!'' Grue swore the second his boat hit land.



``Let me guess,'' Regent remarked to Bitch, ``He's been swearing since we left.''



Bitch nodded.



The Travelers had already arrived.  They stood in a huddle by the water while Genesis disintegrated into several vague floating body parts.



``Coil just bent us over and fucked us,'' Grue said.



``I dunno,'' Tattletale answered.  ``That might have been the only way for him to play things, with the way his power and operations work.''



``That would do a hell of a lot more to ease my concerns if I had any idea what his power was.''



Tattletale only offered an apologetic half-smile and a shrug to that.



I tried to help her out.  ``Look, we \emph{do} know that Coil is smart, he's proud, and he's at his best when he's managing his enterprise.  Being cooped up, he'd be hit hard in all three areas.  Limited tools to work with, limited access to his people, and he'd be less powerful in a way that \emph{everyone} would be aware of.''



``That doesn't excuse how thoroughly he just screwed us, without even \emph{trying} to help us out.''



I shook my head. ``I don't think he's \emph{completely }screwed us over.  We know Coil's got at least one undercover agent, Trainwreck-''



Tattletale interrupted to say, ``He's got a whole lot more than one.''



``Thought he might.  Doesn't it make sense that he'd assist us by being one himself?  I get the impression he likes the control it affords him and the amount of information he can get this way.''



``Maybe,'' Grue conceded.



``We should focus on where we go from here,'' I said.



``Agreed,'' Trickster called out.



Genesis had finished disappearing, and Trickster was walking over to our group, followed by Sundancer and Ballistic.  He extended a hand for Grue to shake, then turned to Tattletale, me, Regent and Bitch to do the same.  Bitch didn't take his hand, turning away to focus on her dogs instead.  Trickster took the snub in stride.  ``If nothing else, I'm glad we get a chance to talk.  Unless things get a lot worse from here, I'm hoping we'll all be working side by side for a little while.''



``Let's hope,'' Grue agreed.



Trickster said, ``We just sent Genesis back in a more discreet form to listen in.''



``Imp is staying behind as well,'' Tattletale informed him, ``So we've got redundancy there.''



``Christ,'' Grue snapped his head from one side to the next, as if he could spot his sister that way.  With a note of alarm in his voice, he asked, ``Imp's still there?''



``She's okay,'' Tattletale reassured him, ``They won't notice her.''



``They \emph{could}.  We don't know how consistently her power works, or if it works in a group that large, and we can't be sure we know \emph{every }power the\emph{ }people there have, if anyone has some extra senses that might bypass her ability.  Fuck!  This is the \emph{exact} type of situation I wanted to keep her away from.  The whole reason I let her join this group was to keep her close enough that I could rein in this sort of recklessness.''



``She's a bit of a rebel, but she's not stupid,'' Tattletale said, ``Trust her to hold her own.''



``I wouldn't trust \emph{myself} to hold my own in her shoes,'' Grue told her.  ``Christ.  Skitter, can you send a few bugs over that way, tell me if she's in one piece?''



I nodded, while Trickster slapped his forehead.



``The bugs,'' he said, ``I could have told Genesis to stick around while you scouted, wait, no.  Why send Imp if you have the bugs?''



``I can't see or hear through the swarm, really.  Not well enough to listen in.''



``You did once,'' Tattletale told me.



That surprised me.  ``When?''



``After the fight with Bakuda.  You were doped up, hurt, you had a concussion, but you were able to tell us the kind of music someone was listening to, and he was way out of earshot.''



``Seriously?  And you didn't tell me this?''



Grue shook his head.  ``Just speaking for myself, I had a lot on my mind, between you and the others being in rough shape and the ABB setting off bombs across the city.  I completely forgot until just now.  Sorry.''



Tattletale nodded.



``That's huge,'' I said, ``Do you know how much I could \emph{use} something like that?''



``Why can't you now?'' Trickster asked.



``Bugs sense things so differently, my brain can't translate what they see and hear into something I can process.  It's all black and white blotches, high-pitched squeals and bass throbs.''  I paused.  ``Imp's perfectly fine, by the way.  At least, I can't find her, but nobody's reacting like they found a spy in their midst.''



Grue sighed, ``Okay.''



``So this sensory part of your power, you stopped trying?'' Tattletale asked.



The way she phrased that nettled me.  ``In the three months between my getting my powers and first going out in costume, I saw \emph{zero} improvement in that department.  None, zilch.  When I did start going out in costume, I was worried the useless sights and sounds might distract me at some crucial juncture.  Between that and the fact that it was like hitting my head against a metaphorical brick wall\ldots''



``You gave up,'' Regent said.  He was trying to get on my nerves, I knew it.



``I \emph{stopped trying}.  But now that I know it's somehow possible, I dunno.  I can start looking for a way.''



The degree to which it would expand my capabilities, it was tempting.  That kind of expansion of my sensory abilities could be a matter of life and death at some point.  I could theoretically listen in on most of the people in my territory.  Would I want to, though?  The invasiveness of that kind of creeped me out, and I had a pretty high creepiness tolerance.



``It might be like your range boosts.  Tied to your mental state,'' Tattletale said.



``Except my range boosts are probably linked to me feeling trapped, and I somehow doubt I felt that way when I was doped up and waking up in that hospital bed or ambulance or wherever.''



``It's something you can work through,'' she said.  ``And now that you know to look for it, you should push yourself to use that part of your power so you can see when it's stronger or weaker.''



I nodded, and willed myself to tear down all the mental barriers and safeguards that walled my brain off from the sights and sounds the bugs wanted to send my way.



It was every bit as grating and annoying as I recalled.  This would take some getting used to.



``Listen,'' Trickster said.  ``Ballistic's HQ is close by.  Since my group is going to be waiting for Genesis, and you guys will want to hang around and pick up Imp when she's done, maybe you want to come by and we can discuss strategy in the meantime?''



``Sounds like a good idea,'' Grue said.  ``Thanks.''



Ballistic gestured toward a nearby street and we all started walking in that direction.



Grue started us off.  ``Number one, we know that they were here to recruit.  Who were they recruiting?''



``Me,'' Regent said.  That drew a few looks of surprise from the Travelers.  He elaborated, ``My sister is their newest member, replaced Hatchet Face.  She did it to fuck with me more than out of a genuine desire to have me join.''



``Armsmaster is another,'' I pointed out.  ``According to Miss Militia, Mannequin wanted him.''



``The, uh, sixth member of the Travelers is the next recruit, I guess,'' Trickster admitted.  ``Crawler hit Coil's place.''



``Sixth?'' I asked.  ``If there's four of you, then-''



``We have two group members who don't see any combat.  They spend most or all of their time at Coil's headquarters.  I understand if that raises a lot of questions, but I –\emph{we}– would really appreciate it if you guys could leave it at that for now.  I'm thinking we'll introduce you to the others soon.''



``I'm okay with dropping it so long as you're not withholding anything crucial,'' Grue said.  ``I'm happy to stay on topic as much as possible anyways.''



Trickster tipped his hat.  ``Appreciated.  Looked like Hookwolf got hit.  His entire group did.  Shatterbird?''



``Yeah,'' Tattletale replied.  ``Can confirm that one.''



``Shatterbird, Crawler, Mannequin and\ldots'' I trailed off, looking at Regent for help in placing the name.



``Cherish.''



``If the condition of Faultline's crew was any indication,'' Tattletale said, ``We can make an educated guess that Burnscar paid them a visit.  Thing is, I can't even begin to guess \emph{who} she visited.  Spitfire's too \emph{nice}, and none of the others really have the, I dunno, \emph{edge}?''



``In any case, that leaves the people who Jack, Siberian and Bonesaw nominated.  Any ideas?''



I glanced across our groups.  Nobody moved to reply.



``Maybe they're not done?'' Sundancer spoke up, ``Or maybe some of them aren't picking new members?''



``\emph{Maybe} they're not done,'' Tattletale spoke, ``But I think they are.  From what I've read on them, and from what my power is giving me, I have the distinct impression they all would have made some kind of move by now.  They either hit all at once, shock and awe, or they draw it out.  This is the former.''



``But are they all picking new members?''



Tattletale shrugged.  ``No clue.  We know of four, at least.''



Ballistic led us into a parking garage.  We walked between rows of cars that had been pummelled by the floodwater.  Panels had been dented, windows shattered, and some of the cars had been lifted and pushed into one another.



Sundancer formed a tiny `sun' and held it up for light, while Regent turned on the flashlight he'd brought.  We descended into the bowels of the garage, and stopped at the ramp between the second level down and the third.  It had collapsed, and both rubble and two or three cars sat in the water that flooded the floor below.



``This way,'' Ballistic said.  He grabbed a length of pipe that stuck out where the ramp had collapsed and climbed down.  Trickster gestured and we moved to follow.



Clever, clever.  Out of sight from any vantage point on the level above, short walls had been set around the fallen ramp.  They ensured that the flooding and the wreckage were all contained to one area to sell the illusion, and kept everything else on the lowest level of the basement dry.  Cars had been removed, clearing the area for use as an underground base.



Ballistic pulled off his mask and tossed it onto the bed that sat in one corner.  He cleared a few dirty dishes from the table in the middle of the area and invited us to sit while he fetched some extra seats.



He had a bit of a heavy brow and a snub nose, and his short brown hair, damp with sweat, made me think of the jocks that always seemed to gravitate towards Sophia.  Still, he wasn't a bad looking guy.  If a guy like him had asked me out in some alternate universe where Emma had never stopped being my friend and I'd never been bullied?  Just going by his looks, I might have said yes.



Trickster unmasked as well.  He definitely didn't remind me of one of the jocks.  His hair was longer than many girls wore theirs, he had light brown skin and an unfortunate hook nose.  Combined with his intense stare, he gave me the impression of a hawk or some other bird of prey.



Grue, Tattletale and Regent all unmasked as well while they got themselves seated.  Trickster offered each of them a cigarette, then offered one to me.  I turned him down, as did the others.



``So what are we discussing here?'' Sundancer asked from behind me.  I turned and saw a rather attractive blonde girl with a long neck and delicate features.  Her hair was expertly pinned up behind her head.  ``I was under the impression that the Slaughterhouse Nine were pretty much unbeatable.''



``No,'' Brian said.  ``Some of them, maybe, but others are as vulnerable as you or me.  Thing is, Dinah told us that our odds against these bastards aren't good.  Our chances of winning are pretty low, and it's pretty damn likely we'll get killed if we confront them head on.''



``So we don't confront them head on,'' Trickster said.



Feeling conspicuous as the only one with a mask on, I pulled mine off.  It took me a second to adjust to the blue tint that everything had after I'd spent over an hour looking through the pale yellow lenses of my mask.  I realized Trickster was setting up a laptop.  He placed it at one corner of the table, facing the rest of us.



``Oliver?''



``I'm here, Trickster,'' a male voice came from the computer.



``Feel like patching in Noelle?''



``Sure.  She's in an okay mood.  A little drowsy.  I'll be right back.''



Trickster pressed a button on the keyboard and then turned to us, ``Tattletale.  I'll be as quick as I can.  Coil promised he'd get you to help us, but he's taken his time introducing you to our group.  The cynic in me suspects there's a reason, and the pessimist in me says that reason is that he's already figured out what you're going to tell us, and it isn't going to be pretty.''



``Okay.''  Tattletale was all business.



``Noelle's going to ask you for help.  Lie to her.  Tell her you're already on it.  Roll with it if she gets angry, or if she gets impatient.  She's sensitive.  I don't know how your power works, really, but if you realize whatever it is that Coil doesn't want us to know, don't tell Noelle.''



``She's the one Crawler visited?'' I asked.



Trickster nodded once.



``Hello?'' A girl's voice came from the computer.  Trickster hit a key, which I assumed was to take himself off mute.  He hit another combination of keys and a webcam feed snapped up to cover the screen.



Noelle had long brown hair and she wore a red sweatshirt.  She looked like someone who was ill.  She was horribly pale, she had dark circles under her sunken eyes, and her lips were chapped.  I was reminded of drug addicts in an early stage of addiction, where they were deteriorating because the drugs took a higher priority than taking care of themselves.  Was Coil drugging her too?



``Noelle,'' Trickster said, ``You've asked to be included more.  I thought you'd be okay with this?''



She nodded.



``Left to right, we have Grue, Regent, Skitter, Bitch and Tattletale.''



There wasn't a flicker of a smile or any interest on her face until she heard that last name.  ``Tattletale?''



``Noelle,'' Tattletale spoke, ``It's nice to finally meet you.  Listen, I'm working on your situation.  Coil's filled me in on the basics and I'm chasing down some leads, but something's come up with the Slaughterhouse Nine, and everything's on hold until we can be sure they won't try to kill us in the meantime.''



I could see Trickster tense.  Was Noelle so high strung or desperate that she'd throw a tantrum over being asked to wait?



``Coil was telling the truth,'' Noelle said, in a small voice, ``You can help?''



``Honestly?  I don't know.  But I'm a fucking genius when it comes to getting answers, and Coil's got all the resources in the world.  If there's help to be had, we'll give it to you.''



``How soon before you know?''



``No idea.  I don't think it'll be as fast as you want, but it's doable, and it won't take so long that you should give up.''



``Okay.''



``In the meantime,'' Trickster cut in, giving Tattletale a thumbs-up gesture from a position outside of the laptop's  field of view, ``We need our old field commander's brain on the Slaughterhouse Nine sitch.''



``A distraction would be nice,'' Noelle smiled for the first time.



Field commander.  She used to be the leader of their group?  I wondered if I could dig up any information about her if I hunted far enough back.



I could see Brian fidget under the table.  He wasn't liking the constant distractions from the subject at hand.



``Eight enemies,'' Trickster said.  ``Now, I'm not a serious player of the game, I'm sorry to any of you Undersiders who are irritated by the way I'm about to butcher it, but the way I see it, their leader is like the king in chess.  More raw power than a pawn, but in the end, he's simultaneously the second weakest piece in the game and the one everything hinges on.  We take him down without getting massacred in the process, I think we win.''



``Jack Slash,'' Noelle said.



``Right.  Siberian's like the queen.  She's fast, mobile, one of the strongest physically, and the bitch of the matter is, she can't be taken off the board, and she can't be contained.  A special queen, if you will.  Physically she's an unstoppable force and an immovable object any time she wants to be.''



To my right, Bitch picked up the puppy and settled it in her lap.  It curled up and nestled against the cupped circle of her arms and hands.



``Then there's Crawler, who visited us the other night.  Maybe not as fast or agile as Siberian, and he \emph{can} be contained, but he can't be taken off the board.  A special rook.''



``I'm wondering how far you can stretch this chess analogy, Trickster,'' Ballistic commented.



Trickster ignored him.  ``Shatterbird and Burnscar are like bishops.  They've got mobility, reach, and they can bury you damn fast if you don't have the right kind of cover.''



``What about Mannequin?  Another rook?''  I asked.



``I'd peg him a knight.  He's more close range, but he'll catch you from an oblique angle, maybe slip past whatever defences you think you have.''



``Which leaves Cherish and Bonesaw,'' Grue said.  ``We'll have to trust Regent to give us the details on Cherish.''



Regent nodded and tapped his finger against his chin, ``My sister.  I don't know if you could call her a third bishop or a knight.  Long range on her power, gets stronger as she gets closer.  Affects your emotions and as far as I'm aware, there's no way to defend against it or to take cover.  If she decides she wants to hurt you or make you hurt yourself, she can find you and she'll make it happen.''



``But she has no special defences,'' Grue cut in.  ``She's vulnerable to pretty much any knife, gun or power we can hit her with.''



``Can we gang up on her?'' Sundancer asked.



``She can affect multiple people at once,'' Regent said.  ``So it's not that easy.''



``That means we have to beat her at her own game,'' Trickster mused, ``Track her, beat her in long-range warfare.''



``I could use puppets to go after her,'' Regent said, ``But she can paralyze them with the kind of uncontrolled physical reactions I can't cover with my power.  I \emph{am} immune to her, for all the good that does.''



``How far does her offensive range extend?'' I asked.



``No clue.  I'd guess she can sense emotions across the entire city, which is how she's finding people, but in terms of attack? I don't have any basis to make a guess.  Farther than my dad, Heartbreaker, but not city-wide, no.''



``The ability to track us by our emotions is a good enough reason to take her out of action ASAP,'' Trickster said.  ``So long as she's active, it'll be that much harder to catch the others off guard.''



``Maybe\ldots'' I started, then I hesitated.  Feeling the pressure of everyone's attention on me, I said, ``\ldots{}Maybe my power will outrange hers?  Not in terms of what we see and sense, but in terms of who can do more damage from further away?''



``It's a thought,'' Grue agreed, ``Risky, but we don't have many options.  Trickster, where does Bonesaw fit into your analogy?''



Trickster shook his head, ``She doesn't.  She's relatively weak in terms of raw power, but her presence on the field threatens to change the rules.  She's a medical tinker.  \emph{The} medical tinker.  So long as she's in play, we can't be certain of our enemy's attack power, we can't know that any enemy we clear from the field will stay gone, and there could be harsh penalties if they catch or kill one of us.  It sucks to think about, but if Bonesaw got her hands on, say, Sundancer, I'd be a hell of a lot more worried than if Hookwolf or Skidmark did.''



Sundancer muttered something to Ballistic, but I couldn't make it out.



``What about our side?'' Noelle asked.



``Lots of playing pieces, not all cooperating, and we have one debatable advantage,'' Trickster said, ``We know in advance, pretty much for a fact, that if any of \emph{us}, Undersider or Traveler, try to fight these bastards, we're going to lose, and we'll lose hard.''



``Tattletale say that?'' Noelle asked.



``Coil did,'' Trickster answered.



\emph{Odd.}  So Noelle was staying with Coil, but she didn't know about Dinah?  Another secret or white lie from her team?



``I can't help but think of the Desecrated Monk scenario,'' Noelle said.  I saw Trickster, Sundancer and Ballistic all nodding.  When I turned to my team, they looked as confused as I was.  Was this Desecrated Monk someone the Travelers had gone up against at some point before they came to Brockton Bay?



``Go on,'' Trickster encouraged her.



``The rules are unfair.  Half of our opponents are pretty blatantly cheating.  But we have to deal with them anyways.  So either we cheat back-''



``Which we can't.''



``Or you guys handle it the way we did it before.  You don't fight the way they want to fight.''



``Okay,'' Trickster nodded, ``So the first question we ask ourselves is how they want to play this.  What do they want?  In terms a five-year-old could understand.''



``They want their ninth member,'' I said.



``Right.''



``They want to hurt, scare and kill people,'' Tattletale put in her two cents.



``Why?''



``Reputation, entertainment,'' Tattletale said, ``These guys are monsters, and pretty much anyone who watches T.V., surfs the web, or reads the papers knows it.''



I saw it out of the corner of my eye.  Noelle's expression shifted all at once from being animated and engaged to the same look she'd worn when the webcam feed first went live.  Disinterested, hurt, hopeless.



She'd been scouted.  Unlike Regent, it hadn't been to mess with her.  It had been because a freak like Crawler legitimately thought she was one of \emph{them}.



If Tattletale was sitting next to me, I would have kicked her under the table.



Noelle suddenly perked up, saying, ``They want to hunt.  They're predators.''



``Okay, how can we use that?'' Trickster leaned forward to look at the screen.



``They want to be the predators, we make them prey,'' Noelle said.  She was looking more animated again.



``Not sure that's possible, but keep going.''



``It's not possible because, um.  You described them like they're chess pieces, and we're thinking in terms of a chess game.  What if we changed the game?''



``I always preferred Go,'' Trickster said, ``But Go is about territory, give and take, less about aggression than an educational sparring match between two master swordsmen, each walking away with a new kernel of knowledge.  Go applies more to taking over the city than it does to this scenario.''



``Shogi?'' Noelle suggested.



Shogi.  I got her meaning almost immediately, and I wasn't alone. Tattletale, the Travelers and I all looked at Regent.



Regent, Bitch and Grue, for their parts, were left looking bewildered.



``Maybe you should clarify?'' Grue suggested.



``Shogi is an Eastern variant of chess,'' I said, ``Some of the pieces move a little differently, though I can't remember how.  But the big difference is that there's a rule that says you can take any of the opponent's pieces you've captured and place them on the board as your own.''



``More or less right,'' Trickster said.



``So the question becomes,'' Grue thought aloud, ``Who can we beat in an \emph{indirect} confrontation, capture and control?''



``Jack, Bonesaw--'' I said.



Grue shook his head.  ``They know they're vulnerable.  Either they'll be watching their backs or the others will watch their backs for them.''



Regent said, ``Siberian is out, and while we might \emph{theoretically} be able to catch and contain Crawler or Mannequin, I dunno if we could keep them still long enough for me to use my power on them.  \emph{If} I can.  Their bodies are different.''



I counted the enemies off on one hand, ``Leaving Cherish--''



Regent shook his head, ``She knows me, has measures in place.''



``Burnscar and Shatterbird,'' I finished.



``The bishops,'' Trickster said.



``Easier said than done,'' Grue sighed.



Noelle's face disappeared from the webcam, and a blond boy popped up in its place.  Oliver?  ``Trickster, Genesis is waking up.  She's done whatever you had her doing.''



``Long stint,'' Trickster replied, ``She'll be groggy.''



``That means Imp is probably done too,'' Grue spoke.



``She'll need a ride back,'' I finished his thought.



``Should leave her there for a bit as punishment for staying behind,'' Grue grumbled.  Still, he stood and pulled on his helmet.  ``But it's not worth the grief she'll give me.''



``Softie.'' Tattletale grinned.



``Are you coming back?'' Trickster asked.



``How long will it be before Genesis is able to brief us on the meeting?''



``Fifteen, twenty minutes?''



``Then we'll be back to finish the strategy session,'' Grue responded.



Trickster turned to his teammates, ``Mind giving Noelle and me a minute to talk?''  Sundancer and Ballistic stood.



Joined by the two Travelers, we made our way up the disguised ladder to the second sub-level of the parking garage.  As one of the last to head up, I saw the adorable sight of Bitch managing the sleeping puppy, tucking it against her body with one arm so she could scale the ladder one-handed.



As she reached the top, I could hear Sundancer cooing, ``It's so cute.  Is it a he or a she?''



``He.''



``What's his name?''



``Bastard.''



``I'm guessing you named him?'' Regent asked, as I reached the top and stepped down onto solid ground.  I missed Bitch's response.  Had she nodded?



``I was surprised you brought him tonight,'' Grue said, being remarkably delicate about the fact that Bitch had undercut any presence our group had by bringing the cute ball of fluff.  It would have been better if he'd brought it up earlier, but he might have felt the same way I did about provoking Bitch before a major event, when she'd been so short tempered lately.



Bitch's response was surprisingly verbose.  ``Had to.  For the first year and a half, he's going to be like a dog.  Need to train him as much as I can, get him used to me.  It'll be too hard if I wait.''



``\emph{Like} a dog?'' I asked.  In the corner of my eye, I could see Tattletale's expression change as she looked at the dog, clearly realizing something.  As fast as I could turn her way to try and piece together what that was, something \emph{else} got her attention.



``Shit,'' she breathed.  She clutched at my arm with one hand and at Bitch's with the other, stepping back to pull us with her.  Bitch pulled her arm from Tattletale's grip, looking angry at the invasion of personal space.



``Oh fuck,'' I muttered, as I saw through the darkness to spot what Tattletale's power had noticed first.



Four of the Slaughterhouse Nine were stepping through the entrance of the parking garage.  The Siberian was in the lead, her waist-length hair blowing in the wind from outside, her eyes practically glowing in the gloom.  Behind her, Jack Slash held Bonesaw's hand as the young girl skipped to make it so she only walked on the yellow lines that divided the lanes.  They were accompanied by a young woman who might've been eighteen or so years old, who bore a striking resemblance to Alec.  Cherish.  None of them wore costumes.  The Siberian didn't wear \emph{anything.}  She was as nude as the day she'd been born, her skin patterned with stripes of alabaster white and jet black.



Jack Slash noticed us, and his his eyes drifted around the arch that led from the parking garage to the wet outdoors.  He smiled, ``This is not an exit.''





