





``This is not an exit.  Kudos for the reference,'' Tattletale said.



``I try,'' Jack replied.  He didn't say anything more, looking us over.  I felt a chill as his eyes stopped on me before moving on to Regent and the Travelers.



\emph{Shit, shit, shit, shit.}  What options did we have?  Running?  Siberian was bound to be faster than the dogs, and none of them were big.  We'd be dead before Bitch got them to grow.  That was even without considering Jack's ability to cut us down from where he stood.



Fight?  Again, Siberian was the biggest problem.  She could take all of us on and win.  I suspected the only people who could really go toe to toe with her would be Scion, Eidolon and the Endbringers, and even then, I wasn't sure if they would really be able to \emph{stop} her.  At best, Scion and Eidolon would survive and keep her from killing any civilians.  The Endbringers would hold their own, but civilians obviously wouldn't be a concern.



Could we escape under a cover of my bugs and Grue's darkness?  I didn't think Siberian would be able to see us, and if we surprised them, ran back the way we came-



``What's this?'' Cherish asked, cutting off my train of thought. ``Someone thinks she's had a clever idea.  A bit of hope and inspiration there.''



``Who?'' Jack asked.



``When I looked at her with my power, before, I called her the Worm.  She spent some time being as low on the food chain as you can get while still being able to move under her own power.  As low as someone can get while still having an identity of their own.  But she's realized she's poisonous, dangerous in her own unique way.  She's \emph{useful}, like a silkworm we harvest or an earthworm who works our gardens.  She's even realized she's not alone, so long as she looks for friends among other dirty\ldots \emph{contemptible} creatures.  Speaking of which, I forgot to say hi, little brother.''



``Fuck you, Cherie.''



Cherish smiled and stared at me, ``The little worm found a nugget of self-worth, she just doesn't want to look too closely at what that nugget is made of.  If she's lucky, she's one of the worms without eyes.  They might be keenly aware of their environment, but they're happier blind.''



``Poetic,'' Jack said.  ``I take it Skitter is this clever worm?''



``Yup.''



``Skitter.'' Jack looked at me.  ``You do \emph{anything} and Siberian attacks.  I'll attack as well.  Whatever it is you're thinking of trying, I'm betting the two of us can cut you down before it works.''



I swallowed, then took a small breath to clear my throat and ensure I wouldn't stammer or come out sounding even slightly unclear.  ``Alright.''



Bad plan anyways.  If we did try to escape under the cover of darkness, Siberian would probably reach us and cut at least \emph{some} of us down before we got anywhere, even attacking indiscriminately.



``The same goes for the rest of you, but I'm sure you know that.  One or two of you could kill me right now, I'm sure, but you'd die horribly for your trouble, and I doubt any of you are that suicidal.''



Did he know about the role he was going to play in the end of the world?  It might change his stance and self-assuredness.



Jack looked at Cherish and she gave him a small nod.  He turned a winning smile towards us.  ``How are our potential recruits doing?''



\emph{Recruits?}\emph{Plural?}  Was he including Noelle?  No.  He would know she wasn't anywhere near here, thanks to Cherish.



Bonesaw piped up, ``I wanted to say hi and meet the people who might be joining the family.  Jack said that if I'm ready, I can tell you what my test is.  Except I haven't decided.''



``Oh?'' Jack looked at her, ``I didn't know you had any ideas yet.''



``I \emph{haven't decided,}'' she told him, sounding annoyed at having to repeat herself.  ``The test might be about challenging \emph{them}, but I'm challenging myself too.  I don't want to be boring, so I'm making myself come up with something original each time.''



``How admirable,'' Jack said.



``And it has to be \emph{fair}.  What I have in mind isn't fair, and I'm worried it's too similar to the test I gave Burnscar.  I need this to be fair.''



``Why does it have to be fair?'' Cherish asked, ``Unfair world, unfair test.''



``Because I like them both!  What better way to add to our family than to have two \emph{real} siblings on the team?  They would fight all the time but they'd really love each other deep down.''



``Ha,'' Regent made it more of a word than an actual laugh, ``You really don't know the Vasil family, munchkin.''



``And the dog girl!  I love dogs!  I've seen the pictures of them and they're beautiful.''



I felt a chill.  All at once, Bitch's presence behind me felt ominous.  She'd been picked by the Nine, and even when asked, she hadn't said a thing about it.  Why?  And who had picked her?  The members of the Nine we hadn't been able to nail down candidates for were Jack, Bonesaw and Siberian.



Siberian, I saw, was staring at Bitch.  When I turned to look at Bitch out of the corner of my eye, I saw her staring right back at Siberian, unflinching, holding the sleeping puppy in her arms.



``If I don't make it fair then it's like I'm picking one over the other and I don't \emph{want} to do that,'' Bonesaw said.



``You're a smart girl.  You'll work it out.''  Jack turned to our group, where we waited in tense silence.  ``A lot going on tonight.  All these meetings, and we didn't get an invitation.  Almost enough to hurt our feelings.''



``Can you blame us?'' Tattletale gave him a shrug.  ``We were talking about how to kill you guys.''



I wasn't the only member of our group to look at her in horror.



Jack laughed.  A little too hard for whatever it was he'd found funny about her statement.  ``Of course, I already knew you were plotting against us, and you knew I knew.''



``Sure.''



``Here is what you need to know, Regent, Bitch.  Each of the Nine's members get to put our recruits up to a test.  Some of us always give the same test, time after time, no matter the candidate.  Mannequin always asks candidates to alter themselves in a way that costs them something.  Siberian waits until half the candidates have been discarded and then hunts the remainder.''



``I hope she doesn't catch you,'' Bonesaw sounded disturbingly earnest as she spoke, ``There's no meat left for me to work with after she's done.''



``As for me,'' Jack said, ``I tend to go last, when all the others have offered their tests and only one or two are left.  I like to mix things up, and unlike our dear Bonesaw, I have no interest in playing fair.''



``And if we fail?'' Regent asked, ``We die?''



``No, no,'' Jack smiled.  ``Nobody passes \emph{every} test, and the punishment for failing a test is up to the individual who assigned it.  Sometimes death, yes.  Sometimes something different.  But it's always \emph{worse}.''



``What did my sister do for her tests?'' Regent asked.



``Hey!'' Bonesaw raised her voice, stabbing a finger in his direction, ``No cheating!''



Bonesaw wasn't the only one he'd irritated.  Cherish glared at him.



``Not cheating,'' Regent said.  ``Call it idle curiosity.  My sister got me in this mess, I figure it would be nice to hear what \emph{she} had to go through.  You don't even have to spoil the answers, I can agree not to copy anything she did.''



Jack laughed, ``Ah, adding to the challenge?  Fair.  She killed Hatchet Face.  Crawler took that as his test completed in advance, didn't think of her as worth his time.  Little Bonesaw, for her test, designed a parasite that would stay in her system for forty-eight hours and strip her of her powers for as long as it remained.''



``Because it's not \emph{fair} that Hatchet Face didn't get to give his test.  And I wanted to break her out of her rut, so I made it so the parasite's effects would be permanent if she didn't drink lots of blood.''



``Of course,'' Jack tapped the heel of his hand against his forehead, ``That was an interesting little twist.  Of course, you didn't tell her how much she needed to drink, or if a certain species counted\ldots  Well.  It broke her stride, didn't it?  Siberian went after her, starting on day two of Bonesaw's parasitic infection.  Three days and three nights of cat and mouse.  To her credit, she did very well.  It came down to a hair.  Another ten minutes and Siberian might have caught her a third time.''



A dark look passed over Cherish's face.



``Shatterbird likes the psychological tests, and she was in a \emph{hell} of a mood after Cherish nominated herself for the team.  Our Cherie didn't have five minutes to rest before Shatterbird drove her into a room and sealed her in.  No food, no light, barely any water.  The room was empty, but for one glass shard.  Always edging towards her, ready to prick, cut, slice and stab the second she stopped, the moment she tried to rest.''



I shivered.  Jack hadn't said how long that lasted, but after three days and three nights without sleep, even a few hours like that would have been nightmarish.



There was a clue there, too.  Credit to Regent for getting Jack to let it slip. Shatterbird had more offensive range than Cherish, if she was able to trap the girl and use the shard without getting affected in retaliation.  It wasn't much, but it was a tidbit of information, a piece for the puzzle.



``Burnscar's test, she failed.  Afraid I'm not spoiling that one.  Doesn't have the same impact if you know it's coming.  That left only two tests for her to pass.  Go on.  Show them.''



Cherish glared at Jack.



``Show them,'' he said.  There weren't any hints of a threat or any anger in his tone, but she obeyed anyways.  She turned her back to us, grabbed the bottom of her shirt and pulled it off.



``Mannequin demands that a candidate changes themselves, and that it be \emph{hard}.  Having just faced the punishment Burnscar gave for failing \emph{her} test, Cherish wasn't about to pay \emph{his}.''



The tattoo stretched from beneath the waist of her low-rise jeans and up the length of her back.  The centerpiece was a large festering heart, done as realistically as any tattoo I'd ever seen.  It was all in shades of green, covered with ulcers, sores, patches of rot and live maggots.  The surrounding tattoos gave the appearance of torn skin revealing the bone and organs beneath, rats and roaches lurking behind ribs and atop her kidneys.  Framing the entire thing were words, not done in any elaborate script, but in scrawled letters that looked like they'd been carved into a surface with knives: epithets and invectives.



``She told the artists to make it so ugly she'd want to kill them.  If she didn't, she promised to kill their loved ones and \emph{then} kill them.  Took six artists in total.  Inspired.''



Cherish looked over one tattooed shoulder to fix Jack with a stare.  It was then that I noticed two things.  The first became clear as her skin stretched.  There was depth to the tattoos that you didn't get with a two-dimensional image.  Her skin had been scarred and flensed to raise edges and give the images and words a permanence that simple ink wouldn't have.



The second thing I noticed was her eyes.  It was like a light had gone out inside her, just standing there with that tattoo exposed.



``That was the hard one for you, wasn't it?'' Jack smiled.  ``Even as tired, scared, hurt and desperate as you were after the other five tests, it was when you willingly defaced that young, unblemished body of yours that a little something inside of you broke, and you began thinking of yourself as one of us.  Liminality.''



``What was your test, Jack?'' Regent asked.  I couldn't tell if he was glad to know his sister suffered or sad for her.



``Oh, I knew it would be almost impossible to top Mannequin's test.  He caught her at the exact right moment, struck the right nerve, and pushed her to her very limits.  Still, I think I managed to top it.  Turn around, Cherish.''



Like an automaton, she did.  More tattoos and scars covered her chest, just as expansive, just as unpleasant to look at.  Two nude women, their entwined limbs like the broken legs of a squashed bug, neither attractive in the slightest.  One was emaciated, the other morbidly obese, and both were old.  More tattoos of rotting and torn flesh framed the scene, and the words forming the border of the tattoos on the front were the opposite of the others, almost worse in their irony and desperation: `Take Me'.  `Please Desire Me'.  `Want Me', and more vulgar variations of the same.



``I made her do the other six tests all over again.''



``I even brought back Hatchet Face for Crawler's test again!'' Bonesaw grinned.  ``No surprise attack that time.  That was one of the three tests she failed in round two, I was so proud of him!''



Seeing Cherish's shoulders draw together, her expression darken as memories came to mind, the ugly tattoos that guaranteed she would never be able to leave this behind and get a completely fresh start, never have a boy look at her body and just be hungry for her\ldots I had to look away.  I knew she was the worst sort of person, I just didn't know how much of that came before the tests.



``Well, sis,'' Regent said, ``I thought you were running headlong into a fate worse than death.  I stand corrected.  You're already there, and you did it to yourself.''



She pulled on her shirt and snarled, ``This is the part where I'd threaten to kill you, except \emph{they }are going to do it so much better than I ever could.''



``Can't do it yourself?'' Tattletale cut in.  ``Why do you have to rely on them?''



Cherish's eyes narrowed.  ``You're trying something.  I feel smugness from you, too much confidence for where you're standing.''



Jack smiled and caught the hairs of his beard between his thumb and index finger.  ``Oh?  I'm still interested to hear your answer to her question.''



``Fuck that.  You're getting predictable, old man.  You want to keep things amusing for yourself, you know you're as smart as anyone else in the room, so you take the hard road so it won't be too easy.  Why not have Siberian eat her?  Can't you imagine the looks on her friend's faces when they can't do a thing to save her?  I bet it'd light a fire under their asses, rev them up for the tests.  Maybe they'll even throw themselves headlong into it, to spare the rest.''



``Now who's trying something?'' Tattletale asked.  ``She's trying to manipulate you.''



Jack frowned and yanked out the hairs of his beard he was holding.  He flicked them away, ``I \emph{know} she's trying to manipulate me.''



``Okay, except I just noticed something else, as I finished that last sentence.  Do you \emph{know} she's playing a long con?  She's setting you guys up, using her power to pull your strings and make you attached to her.  Half a year to a year, she'll probably have you wrapped around her little finger,'' a slow smile spread across Tattletale's face.



I could see Cherish's expression change from anger and irritation to wide-eyed horror.



Jack pinched the bridge of his nose, looking down, and I could just barely hear him mutter the word, ``Disappointing.''



``It was probably her plan from the start,'' Tattletale said.  ``She-''



All at once, Tattletale stopped talking, and I was blind.  In that same instant, something slapped against the fabric of my mask.  Wet.  I could taste it against the fabric of my mask.  Salty-sweet, with a faint metallic taste.



``You fucking bastard!'' Grue shouted, his voice distorted by his power.



\emph{Blood.}



I hurried to wipe it from the lens of my mask.  Everything I saw was obscured by the streaks that remained, almost black in the light.



Tattletale lay on the ground a little in front of me, both Regent and Sundancer crouched at her side.  So much blood, covering her face and Regent and Sundancer's hands.



Jack toyed with the knife in his hands, while Siberian stood between him and the rest of our group, her eyes primarily on Ballistic.



Jack paced back and forth, two or three steps at a time, gesticulating with his knife.  ``I was looking forward to Cherish's attempt.  Bonesaw and I even had a plan in mind.  I wanted to see what she did, how she worked around Siberian's immunity to her power\ldots then the safeguards Bonesaw implanted in us would have kicked in and released us from her thrall, and oh, the look on her face.  To have seen that would have been so very worth all the trouble.  And that \emph{girl} just spoiled it all.''



``You know,'' Cherish said, shell-shocked.



``Clearly.''



``But my power – I didn't sense anything as far as your planning, your emotional networking or-''



I dropped onto my knees so fast it hurt, and immediately began trying to help Tattletale, and Regent gave me the space, allowing me to take over.  Jack had cut her from her mouth to the edge of her jaw.  It had parted the skin at the corner of her mouth.  I must've been directly in the line of fire for the resulting blood spray.  How was I supposed to put pressure on a wound like this?



Jack was getting heated, talking mostly to himself.  ``That was the whole point!  To see how long we could go without tipping her off.  Bonesaw helped with some surgery, even some artificial neural connections that Cherish wouldn't be able to see.  So much work and preparation ruined.''



``I-'' Cherish started, then stopped before she could finish the sentence.  Trying again, she asked, ``What are you going to do with me?''



``Not a pressing concern,'' Jack said, as if realizing she was there.



My power crackled at the edge of my consciousness.  I had to suppress it, before I gave them another excuse to attack us.  The majority of my attention was on Tattletale, on Lisa. I used my fingers to scrape as much of the blood out of her mouth and throat as possible, then adjusted the angle of her head so any further blood would flow down the side of her face or out of her mouth.



The fabric of my gloves afforded more traction than fingertips would have, but the amount of blood made everything slick to the point that I couldn't be sure of what I was holding.  I had one hand inside her mouth, her teeth hard against my knuckles, my other hand pressing down from above to sandwich it and press everything as closed as I could get it.  She roused herself enough to pull away, no doubt because I was pulling the tear at the corner of her mouth open.



``Hold her head, Regent, don't let her pull away.  And cloth,'' I said, my voice small, ``Need some kind of cloth to absorb the blood.''



First aid classes hadn't prepared me for this.



There was a tearing sound, and regent handed me a strip of cloth.  I fumbled to put it into place at the corner of her mouth, where the bleeding was worse, then applied the rest along the cut.  The white cloth turned totally crimson in a second.



``More,'' I said, keeping my voice quiet so it wouldn't carry to the members of the Nine that were standing nearby.



``I wouldn't bother,'' Jack said.  ``A wound like that, she'll die of blood loss before you can do anything.''



``You asshole,'' Grue growled.



``You really shouldn't swear!'' Bonesaw said.  ``It's crude!  If you agree to be good, maybe I could fix her for you.  Oh, and since her cheek's already cut, I could change it around so her teeth are on the \emph{outside} and she wouldn't have all that skin and flesh just getting in the way.  And, and, I could make it really artistic and beautiful, and change her tongue so she can make all of the speech sounds you'd normally need lips to make, like puh, buh, muh, wah, vuh\ldots''



Regent handed me more cloth, and I wadded it into place.  Tattletale wasn't really moving, and I couldn't be sure if it was because of the amount of blood she had already lost or just because it hurt too much.



I saw a flicker of light as Jack flicked his knife out, tossed it into the air and then caught the blade tip between his middle finger and the nail of his index finger.  He snapped it around so he gripped the handle.  ``I suppose I should get around to the purpose of our meeting you here, Regent and Bitch.  Unless you want to pose your test to them, Bonesaw?''



``No.  Let me think about it for a little while.''



``Alright.  Well, it wouldn't do if our candidates died before we even got around to the tests, so I came to offer you two a warning.  Two warnings, as it happens, for each of you.''



Why couldn't he stop talking so we could take Tattletale somewhere where she could get the help she needed?  My hands were already cramping from trying to maintain pressure and the awkward angle that resulted from  the way I had her head tilted.



``Two of the candidates we chose are heroes, for lack of a better word, and Cherish reported that we may have trouble bringing them in close enough to introduce them to the tests.  Our dear Bonesaw has devised an \emph{incentive }to encourage their cooperation.''



Bonesaw reached into her pocket and withdrew a small vial.



I felt Tattletale tense and looked down.  She was staring at the vial.



``Biological warfare?'' Grue asked.



``Naturally.''



``What does it do?''



``Just in case all of our candidates fail to play along, I would strongly advise you to stick to bottled water.  No filtered water, no rainwater, none of that.  Not unless you're feeling brave.  Just to be on the safe side, avoid getting your injuries wet as well.''



``And the second warning?'' I asked.  I wanted him to finish.



``In\ldots'' Jack pulled out a pocket watch on a chain. ``T-minus thirty-four minutes, Shatterbird is going to sing loud enough for much of the city to hear her.  She wants to make it known to everyone in Brockton Bay that we're here, and since there's no need to maintain surprise with our potential members, I said she should.  With this in mind, you would be well advised to stay away from anything made of glass or any beaches, and be sure to put away anything in your pockets with a screen.''



\emph{Dad}.  The people in my territory.  I had to warn them, but\ldots



I looked down at Tattletale and felt paralyzed.



``That's the meat and bones of it,'' Jack smiled, ``It was nice to meet you two.''



I felt Tattletale move.  Her hand was fumbling at her belt.  Was she going for the gun in the largest pouch?  No.  A pouch near there, just as long, but thinner.



``Sundancer,'' I hissed, ``Help her.''



Sundancer did.  There were pens in the pouch.



``Help her find the paper,'' I said.  Jack and his team had wrapped up and were walking away.



It was a notepad barely larger than a pad of post-its.  Tattletale took the pen that Sundancer held for her, clasping it in a closed fist.  She scrawled out one word.  `Deal'.



Then she looked up at me, her eyes wide.



``No,'' I whispered.  ``We have to get you help, and I have to go warn-''



She stabbed at me with the pen and clenched her teeth against the back of my hand, which must have caused her incredible pain.  I wasn't sure if it was her pain and mine, but Cherish turned and gestured for Jack, who was already walking way, to stop.



``A deal,'' I called out, ``I don't-''



Sundancer had ripped off the first sheet, and Tattletale was writing the next message.



I swallowed, ``She wants to know what happens if\ldots if more than one person is left at the end.''



``We pit them against one another,'' Jack said.



The next word- I could barely make it out.  `Game'.



``She, um.  I think she wants to play a game?''



Tattletale gave me a single, slow blink of confirmation.  She was writing more.



``A game?'' Jack asked.



I couldn't make sense of it.  `If there more half left at end.'



``One second.''  I said.  Sundancer ripped off another sheet.  This was excruciatingly slow, trying to parse her shorthand and follow her line of thought.  ``Tests.  If there's more than half of the candidates left at the end of the tests, we win.  You leave with volunteer?  You could leave with whoever wants to join.  But you leave.''



``You expect that half of the candidates could pass the tests?  I'm intrigued.  I don't think it's possible, but I'm intrigued.''



``Brockton Bay has its share of badasses, Jack,'' I said, my voice hard with repressed outrage.



``I don't see what \emph{we} get out of it.''



Tattletale had dropped the pen.  It was up to me to pick up the slack.



``It's a challenge.  A game.  Changing the routine.  We can do whatever we need to, to keep as many candidates alive as we can.  You guys\ldots do what you do.  It keeps things interesting.''  My eyes fell on Bonesaw, ``And maybe it keeps things fair?''



Seconds passed.  I felt the tension ratcheting up another notch with each beat of my heart.  Every moment that passed was one step closer to Tattletale bleeding out or to Shatterbird using her power.



``I like that.  It might be a way to fix the test I want to give.  Let's do it,'' Bonesaw said, looking up at Jack.



He frowned.  ``We'll discuss it as a group.  I suspect we'll have terms of our own to attach to this game.  Among other things, a steep penalty for when \emph{we} win.''



And then he turned to leave.



I looked down at Tattletale.  Her eyes were closed.  My hands felt like two blocks of stone where I had them pressed to her injury; rigid, heavy, unable to move.



``I don't know what to do,'' I said, barely audible to myself.  I looked up at Grue and said, louder, ``I don't know what to do.''



He didn't have an answer for me, but he bent down to check on Tattletale.



It was Tattletale who gave me my orders.



``Guh,'' she coughed out the word.  As Grue gently pulled my hands away to take over, she repeated, only slightly clearer, ``\emph{Goh}.''



\emph{Go}.



I stood, wobbling slightly as I backed away from her.  She looked so fragile, lying on her side, blood pooling beneath her head, around her dirty blond hair.  And I was leaving her there.



``We can call Coil,'' Ballistic said.  ``He can send a car to get you where you need to be.''



I shook my head.  I couldn't wait and trust that a car would arrive in time, or that it would get me where I needed to be.  There would be detours, areas a car couldn't pass through.



I turned and I started running.  Out of the parking garage, past Cherish, Bonesaw and Jack.  They didn't say anything, and they didn't try to stop me.



I was a block away from them when I got my cell phone out and dialed home, but I already knew the response I would get.  The automated message came from the phone as I held it in one hand, heading directly north.



\emph{This phone number is currently out of service.  If you would like to leave a message\ldots}



Judging distances wasn't a great strength of mine.  How many blocks, how far did I have to run to reach my dad?  Five miles? Six?  I was a practiced runner, but the streets here weren't all in the best shape.  Some were flooded, others strewn with debris, still more suffering in both departments.  There were areas that were blocked off.



And I had less than thirty minutes.





