





\emph{I could kill them right now}.



It would be so easy.  Jack, Bonesaw and Cherish were all in my range.  I could drop poisonous spiders on them, sting them each with dozens of bees and wasps in the hopes of provoking anaphylactic shock.  It would be \emph{easy}, and I might save the world by doing it.  I'd get revenge for the countless people they'd murdered, for their attacking Tattletale, and maybe even save hundreds of people's lives by distracting Shatterbird.



But I wouldn't be able to kill Siberian.  She'd fought Alexandria, Legend and Eidolon at the same time and walked away unscathed.  She hadn't been able to hurt them due to her inability to fly, but she'd still survived.  If I attacked Jack, she would come after me and I'd probably die.  Would it even work?  Bonesaw was a medical tinker.  She could theoretically save all three of them.  Then I'd accomplish nothing but getting the Nine pissed off at me.



If it was just my life at stake, a part of me hoped I might do it anyways. But it wasn't.  Others would pay the price if I got away from Siberian, and maybe even if I didn't.  Even if I escaped and Siberian didn't get her hands on any of us, the added distraction and detours that came with evading her would probably mean I couldn't make it to my dad in time.  And if I \emph{did} die, Dinah might never go free.  Which only led to the greater question: would I be willing to trade ten lives for the hundreds or thousands those members of the Slaughterhouse Nine might potentially kill if they walked away here?  The \emph{billions}, if Dinah's prediction about Jack came true?



I remembered what Brian had said back when we'd found out about Dinah: the choices we made in terms of who we tried to save: those we cared about versus complete strangers.  I'd rebelled at the idea of people abandoning people to their fates simply because they didn't know them and weren't connected to them in any meaningful way.



But now that I faced having to make the call and decide if my life and the lives of just about everyone I cared about were worth less than everyone else's, it didn't seem so black and white.



The decision to attack and kill Jack and potentially sacrifice our lives in the process wasn't binary, I told myself.  It wasn't limited to two options.  I would try to save the people I could tonight.  Then our teams could \emph{collectively} prepare to do something about Jack and the other Nine, after we were all ready to defend ourselves.  As much as a small part of me wanted to make the heroic sacrifice, I couldn't throw away my life for the mere \emph{chance }to kill him, and I definitely couldn't throw away the lives of others.



The inch deep water splashed as I ran, my feet already sore from the impacts against the pavement.  The soft soles of my costumed feet made me quieter when I walked, but it wasn't fit for running.



How much of my decision just now had been because I didn't want to kill a man?



I was indirectly responsible for the deaths of others.  I'd looked at the information on the capes who'd died during Leviathan's attack and found Chubster, the fat man I'd failed to save.  Innumerable others had died because we hadn't been able to stop Bakuda, giving her the chance to attack the city, killing forty-three people and inflicting horrific injuries on dozens more in the process.  When Thomas, the man from the Merchants, had been bleeding to death, I'd given the order to leave him there to die.



There were others, too, I was sure.  A part of me was horrified that I couldn't even keep track of it all.



At the very same time, another part of me was just as horrified at the idea that I might \emph{not} have the ability to pull the trigger, to deliver the venomous payload or drive the knife home.  So much could hinge on that.



I shook my head.  \emph{No}.  I didn't want to dwell on the subject of murder.  I had to \emph{save} people.



The upper downtown area had no power, and it was just warm enough that people had their windows open to get some reprieve from the heat.  That made it easier.  I sent some bugs into every open window, using the roaches and flies that were already present when possible.



How many people did I have to reach?  The buildings here were anywhere from six to twelve floors, and there were anywhere from one to six apartments to a floor.  Less than half of the apartments were occupied following the evacuations, but it still made for hundreds of people on each city block.



I didn't slow my pace as I worked.  Bugs swept over the surfaces of rooms for any smooth surfaces that indicated glass or mirrors.  I checked bedside tables for eyeglasses and alarm clocks.  If I found glass, a bed positioned too close to a window or mirror, something potentially dangerous on the bedside table or if there were enough attack bugs around, I attacked the residents.  The bugs bit, stung, or momentarily smothered them, covering their noses and mouths, waking them.



Hundreds of people at a time.



It dawned on me as worked through each bedroom in each apartment: I doubted there were five other people in the world, cape or not, who could multi-task like I was.  It \emph{had} to be a side-benefit of my power.  My consciousness divided a hundred ways, problem solving, performing complex tasks for a hundred different scenarios at once.



Once each person was awake, I had to warn them.  But that wasn't simple – apartments without power didn't have light, either.  For many, I could put the bugs on the window and spell out words with their silhouettes, but there were people with blinds and curtains that would obscure that.  I forced myself to use the bug's sensory inputs, to seek out the biggest patches of light and warmth in each room where a person was being woken up, so the bugs could cluster in those spots and hopefully be seen.



But what could I write?  I looked at my cell phone to see how much time I had left. For some, where I had enough bugs and space to write, I told the bugs to spell out `Glass explosion 28 min'.  For the places I didn't, I spelled out `take cover' or `hide under bed'.



Thousands of people, a thousand warnings.  I couldn't be sure that everyone saw or listened and I couldn't hang back to make things clearer or pass on more detailed information.  It was stupid and selfish, but I had to reach my dad.  Not for any greater plan or for the greater good, but for \emph{me.}  Because I wouldn't be able to live with myself if I didn't.



And even this, helping people here, striving to help my dad, wasn't the extent of my responsibility.  I selected Sierra from my contact list and called her, trusting my bugs to give me a sense of anything I might run into or trip over while my eyes were on the screen.



``Yes?''



``Where are you?''



``Hospital with my parents and Bryce.  You said I could have the night off, that you'd be busy.''



I was short on breath from the running.  ``Emergency.  Shatterbird's about to hit the city.  Twenty-seven minutes.  Warn the hospital, now.  Convince them.''



``I'll try,'' she said.  I hung up and dialed Charlotte.



``Skitter?''



``Twenty-seven minutes and change before Shatterbird hits the city with her power.  Spread the word, \emph{fast}.  Avoid glass, take cover from a potential sandstorm.''



``The \emph{Slaughterhouse Nine are here?}''



``They've been here a little while.  Go!''



``I don't\ldots \emph{how}?  How do I tell everyone?''



``Tell as many people as you can, tell \emph{them} to tell as many people as they can.  Now go!''  I hung up, to force her to move sooner and because I couldn't spare the breath.



My range and fine control were extending.  This not only kept the people behind me in my range for a precious few extra seconds, but it extended my range forward and to either side, adding one hundred people to the total who fell within my range.  Soon that became two, three and four hundred more.



My legs burned, my feet throbbed, and I could feel sweat soaking the fabric of my costume where the water I was running through didn't.  On one block, the water would be only a half-inch deep, but the next might prove to be nearly a foot in depth, adding extra resistance to each movement of my already complaining legs.  The block after that, it could just as easily be a split-second decision between trying to make my way past the piles of rubble and parked cars and detouring to the next block over.  Which would cost me more time?



If only Bitch and I were on better terms, maybe she could have explained about the Nine approaching her.  If I could only trust her, if she could only trust \emph{me}, I could have borrowed one of her dogs, and this wouldn't seem as impossible as it did now.



I made my way through the college area that was Regent's territory.  The buildings here were in rougher shape.  There were fewer people to warn, but they were harder to find.  I used the bugs I could afford to check my way was clear.  Five blocks ahead of me, I could feel the presence of construction equipment, of temporary fencing and barricades.



Chancing a look at my phone, I felt a chill.  Time had flown while I'd worked, my attention elsewhere.  I had eleven minutes, and I wasn't close enough.  I couldn't afford to take a detour.



I threw every bug that wasn't warning someone at the fencing, flying insects gripping the thin metal bars, crawling insects swarming at and under the concrete pads beneath each post.  Tens of thousands of bugs gathering together to surge forward as a single mass.  I tried pushing, pulling, trying to rock it and build enough momentum with the bugs to bring it down.



My bugs hadn't managed to push it over by the time I reached the fence.  It had been designed to withstand strong winds, and the concrete feet at the base of each pole gave it too much stability.  As I got there, I had to stop running for the first time, panting for breath.  My fingers clutched the grid of fine metal wire until it hurt.



The thin metal wire pressed hard against the deep tissue of my gloved fingers as I climbed the fence, while my toes scrabbled for a hold on the metal hinge that divided one section of fence from another.  Precious long seconds, maybe a minute or two and I knew I'd have to get by the fence on the far side as well.  I wobbled on top of the fence and then hopped down with a splash.  I was running again the second I had my feet under me.



Why wasn't I stronger?  My disappointment in my luck and the power it had given me was an almost physical pain.  I could warn people, but I couldn't push down a fence.  I felt cheated.



I managed to squeeze between the edge of the second fence and the neighboring building.  My phone showed the time as 12:33 at night.  I had seven minutes.  Something as \emph{stupid} as fences had cost me so much time.



That doubt and fear that had rested with me the second I'd realized how far I'd need to travel in this short span of time was crystallizing into a dawning realization that I wasn't going to make it.



The window of opportunity for getting to the house and getting my costume off and getting dad somewhere safe was long gone.  Even the window for doing all of that \emph{without} taking the time to get my costume off was long past.  I was too far away.



That left only one option.  Could I save him with my power the same way I'd been trying to do with everyone else that fell in my range?  I still needed to get closer, fast.



I held my phone in one hand, sneaking glances as I made my way from one block to the next.  The six-minute mark came all too fast.  The clock on my cell phone ticked to 12:36.  Four minutes left.  Three.



Then I couldn't look anymore. I threw it aside, trusting my bugs to nudge it into a storm drain where it wouldn't be found.  The time wasn't exact; I couldn't be sure \emph{exactly} how much time had passed since Jack had told us about Shatterbird's attack.  I couldn't say if Shatterbird's clock was a few minutes fast or a few minutes late.  There was no point on dwelling on the final minutes, and keeping my cell phone on me was dangerous.



That, and I wasn't sure I could bear to watch the clock hit zero.



I heard sirens nearby.  Not just from one vehicle, but several, all getting closer.



I could sense my neighborhood, and the black widows that were still where I'd put them.  Every step brought more bugs into my focus.  Ants beneath people's lawns, earthworms in gardens, pillbugs and earwigs under stones and objects in garages and carports, cockroaches in the darkest corners of cabinets.  I woke the people I could and left them their warnings.



I knew the time had to have run out.  But I was \emph{so close}.  I could sense the block my house was on, the neighbor's house.



And then my dad's house.  I dropped onto my hands and feet the second I was in range, my legs aching.



My bugs swept over the interior.  I knew the layout, so it was quick.  Dad was in his bed, bundled up in the covers.  He was taking up only one side of the bed, leaving the space that mom had once occupied empty.  It was like a punch in the gut, a reminder of how alone he was.  How alone I had left him.



I needed more bugs to wake him, still more to write a message.  I began drawing them up to his bedroom.



I might not have noticed it if I hadn't been listening through the bugs.  I primarily heard it through the moths and beetles, a sound like someone running their finger along the rim of a wine glass, painful to hear, only it kept getting sharper and higher pitched until it was well beyond the limits of anything my human ears could hear.  It was coming from the windows.



There were enough bugs in place to wake up my dad.  I could have disturbed him from his sleep\ldots but would he react fast enough to any message I left?  Or would he sit up and put his head and upper body in harm's way of the windows?



I couldn't risk it.  Instead, I took the bugs near him and threw them against his alarm clock, a miniaturized version of what I had attempted to do with the temporary fence.  It was thin, a tilted capital `L' shape with a digital display.



I pulled my knees up against my face and my hands up around the back of my head to shield myself where my mask didn't have coverage.



The alarm clock was in the midst of tipping over when Shatterbird used her power.



It was as though the glass broke in response to some invisible tidal wave, caught in the nonexistent `water', carried along, shattering on impacts with surfaces, slashing anything that would cut, piercing deep into any surface soft enough.  I could feel it roll past me, south to north.



\emph{Loud}.



The sound seemed to come a second later, like the sonic boom following a jet.  I'd halfway expected a boom, but it sounded more like a heavy impact, as loud and powerful as a bullet the size of the moon striking the city, followed by the sound of trillions of glass shards simultaneously falling like rain across the cityscape.  There was a cloud to the east, where the beaches were, reaching up to the cloud level, like some pale wall.



The moment I was sure it was over, I was on my feet, running around the back to the kitchen door.  I tore off my mask as I made my way there, and some bugs helped guide my hand to the latch as I reached through the broken window of the kitchen door and opened it.  I tore at the straps connecting my armor to my back as I ran upstairs, taking the steps two at a time, pulled the zipper down as I ran down the hallway.  Getting my arms free of the sleeves, I tied the inside-out arms around my waist.  It wasn't nearly enough to seriously hide my costumed identity, but I wasn't about to delay for another second.



I pulled open his bedroom door and hurried to his side, glass crunching under my feet.  I gingerly peeled away the layers of blankets that had draped over my dad as he was thrown from the bed.



So much blood.  Two thirds of his face was covered in blood that looked more black than red in the gloom.  Darker lines marked where the blood was welling from.  Cuts across the side of his head, the edge of his forehead, his temple and cheek.  His ear had been almost cut in half.



There was a rattling from the window.  I looked and saw strips of shredded duct tape.  It looked like the tape had been taped around the edges, then taped in an asterisk-like pattern.



He'd taken my warning seriously.



I investigated further.  More blood at the back of his head.  Had the glass penetrated into his brain?  No, I could feel the edges of the glass.  It had stopped at his skull, maybe splintered under the surface of his skin.  I had no way of telling.



His hands fumbled blindly for my wrists, seized them.  He couldn't see me with the blood in his eyes.  That fact didn't make me happy or relieved in the slightest, however it might have kept him from discovering my costumed identity.



``Taylor?''



``I'm here.  Don't move too much.  I'm going to see what I can do.''



``Are you okay?''



``Not even scratched.''



I could see him sagging with relief.



``You were right,'' he said.  He tried to stand, and I pushed him back down.



``Stay still,'' I said.  ``At least until we can be sure there's nothing more serious.''



``Right,'' he mumbled.  ``You took that first aid class.''



More glass had penetrated his blankets and sheets.  There were holes in his back, his arm and shoulder.  All bled, but none seemed to have hit any arteries, gushing or releasing copious amounts of blood.  It was still far more blood loss than I would have liked – his undershirt was turning crimson.



I climbed over him, glass stabbing my palm as I put a hand on the ground for balance.  I wanted a closer look at his back.  Had anything hit his spine?  \emph{Fuck}.  There was one hole close to the spine, around the same distance down as his belly button.



``Can you move your toes?''



There was a pause.  ``Yes.''



I breathed a sigh of relief.  ``Then the next biggest issue is possible internal bleeding.  We need to get you to a hospital.''



``They hit the entire city?''



``I think so,'' I told him.  No use letting on exactly how much I knew.  It would only cause the both of us more distress in the long run.



``The hospitals will be overcrowded.''



``Yeah.  But \emph{not} going isn't an option.''



``Okay,'' he said.  ``I'll need my sandals, downstairs.''



I was using my power to find them by the time I was standing again.  I found something else.  There were people in our kitchen.



\emph{The Slaughterhouse Nine?  }Had they followed me here?



My dad was unable to see, thanks to the blood.  I drew my bugs together into a cluster, hid them in the folds of my costume, which I had tied around my waist.  I crossed the hall to my room and found a pair of loose-fitting cargo pants from when I'd had a bit of a belly and a wider waistband.  I zipped up the pants and tied a sweatshirt around my waist to hide the rest of my costume.  I could sense them approach.  One of them waved at a fly that flew too close to their head.  Both were men.



Floorboards creaked as they ascended the stairs.



``Hello?'' one of them called out.  I tensed.  I didn't recognize the voice.  They were right by my dad's bedroom.  I heard my dad respond and swore under my breath.



My knife was still strapped in against the back of my costume, which dangled around my knees.  I bent down and drew it from beneath my sweatshirt.



Voices.  One of them murmured something, and my dad replied.  I couldn't make out anything in terms of the words or the tone of what they were saying.



Quietly, aiming each footstep to avoid the worst patches of broken glass, I stepped from my bedroom, my knife held low and ready.



Two paramedics were working together to shift my dad onto a stretcher.  I hurried to put the knife away.



One noticed me.  ``Miss?  You're alright?''



``I'm fine.''



``This your dad?''



``Yeah.''



``We're going to take him to the hospital.  Mind making sure our way out is clear?  Maybe open the front door for us?''



``Okay.''



I felt like a machine, clumsy, almost emotionless, as I led them out of the house.  There were two other ambulances parked in places I could see.  None had windshields, mirrors or headlights.  The explosion had blown out the flashing lights and whatever system had handled the sirens.



It didn't fit.  The timing of this, their preparedness.



But they didn't look like any members of the Nine I knew.  I could see one of the paramedics down the street – she was black.  So it wasn't the Chosen, either.  Merchants wouldn't be this organized or devious.



I reminded myself of where my knife was, in case I needed to draw it at a moment's notice.



The two paramedics began loading my dad into the back.



``Can I ride along?'' I asked one, the second they were done.



He looked at me, then grabbed something large, black and irregularly shaped from a pocket beneath the stretcher.  Holding it in one hand, he put one hand on my shoulder and led me a short distance away.  My heart rate tripled.  My gut was telling me they weren't normal paramedics, and this was the moment I found out just how.



``Here,'' he pressed a bundle into my hands.  It was large, bulky, and there were hard bits beneath the cloth.  ``You don't want to leave this behind.''



I peeked at the contents of the bundle, then swallowed hard.  It was my mask and the back sheath of my armor with the stuff inside.  In my haste, I'd torn them off and left them where they fell.



``You're with Coil?'' I asked.  I felt a quiet horror at the realization that Coil would now know who my dad was, and who I was by proxy.



He nodded once.  ``More specifically, your teammates sent us.  They'd hoped we would pick you up and drive you here, but we weren't able to find you, and we were delayed  because we had to take safety measures first.''  He looked towards the van.  I realized he was talking about the removal of the glass.



Relief surged through me, and I felt tears welling up.



That relief proved short-lived.



``Our \emph{employer }feels there's very little you'll be able to do with your father here, and quite a bit you could do \emph{elsewhere.}  He did say he understands if you want to prioritize your family.''



My eyes widened in understanding.  Coil wanted me to attend to my territory, now, in this moment of crisis.  ``He wants me to leave my dad?''



It might as well have been a rhetorical question.  The paramedic didn't respond.  I felt my heart sink.



``We'll give him the best care we can,'' he said.



I turned and climbed into the ambulance.  My dad was gingerly dabbing at one of his eyes with a wet cloth.  I was pretty sure he didn't see me.



I bent over him and kissed him on the corner of his forehead, in a spot where the blood didn't cover his face.  He snapped his head up to look at me.  The white of one of his eyes had turned crimson, the green of his iris pale in the midst of it.



``I love you dad,'' I said, then I backed away a step.



``Stay,'' he said.  ``Please.''



I shook my head.



I stepped back once again, and then hopped down from the back of the ambulance, turning away.



``Taylor!''



Always like this, now.  Always walking away, knowing how much it hurt him.  I blinked more tears out of my eyes.



``You make sure he's alright,'' I ordered the paramedic, ignoring another of my father's shouts.



The man nodded.  ``I can tell him we aren't allowing ride-alongs, just in case we need more bodies in the back.''



``Thank you.''



My power buzzed at the edge of my consciousness as I turned my back on the scene.



Fuck all of this.  Fuck the Nine.  Fuck Shatterbird.  Fuck Jack.  Fuck Leviathan.  Fuck Coil.  Fuck Hookwolf.



Fuck \emph{me}, most of all.





