





Mannequin lunged for me, his bladed toes biting into the ground for traction.  He moved fast enough that his arms trailed behind him like twin ribbons in a strong wind.



He stopped several paces away from me, turning his body to swing at me with his right arm and the three foot long blade that was attached to it.  If I hadn't known better, I would have thought he'd fall well short. But his arm extended on a chain, giving the swing just enough reach to put the blade on a collision course with my head.



I parried it with my baton.  The hit was \emph{heavy}, more like trying to fend off a sledgehammer than what I'd expected.  I almost lost my grip on my weapon.



As the blade bounced off my baton, he reversed the direction his upper body was turning to start spinning like a top.  His one attached arm hurtling around him, he sprung at me.  I threw myself back and away, escaping by a mere two inches.



His spinning upper body had, with his right arm spooled out, caused the chain to wind around his body.  He began reeling it in, the arm and blade drawing a lazy circle around him.  I backed away, thinking I finally had a chance to get my bearings.



As his detached arm reeled in, the fingers folded backwards around the end of one of his feet, gripping it.  He retracted the blade at the toe of the other foot and dropped that foot flat on the ground.  The motion seemed to unbalance him, and he teetered, almost falling over.  Then in one sudden motion, he righted himself and thrust out with his other leg and the three-foot blade that was now attached to it.



I didn't have time to get out of the way, to bring my baton up to defend myself or even to do more than belatedly realize his near-collapse had been a feint.  He caught me in the stomach with that same surprising strength as before, then slashed up toward my collarbone with enough force to lift my feet up off the ground.  I landed hard on my back, my armor absorbing the brunt of the impact.  The sides of my armor panels bit into the ribs of my back where they curved toward my body.



Keeping the lessons I'd learned from sparring with Grue in mind, I tried to scramble back and away while Mannequin righted himself and put the forearm and hand he had connected to his foot in the right place.  Before I could get to my feet, he started striding toward me.



I drew my bugs around me to conceal my movements as I rolled to one side, set my feet under me and sprinted to his left.



While still beneath the cover of my bugs, I was struck from behind and knocked face first to the ground.  The surprise was as bad as the pain.



Through the swarm, I sensed him approach until he stood with one foot on either side of me.  I felt him wind his fingers into my hair and pull my head up and back.  I struggled, trying to catch him in the knee with my baton, but he wrenched me to one side, and I felt a blade press against my throat.



As he'd done with the gray-haired doctor, he pulled the blade hard against my throat in one long, smooth motion, adjusting for the curvature of my neck.



In one heartbeat, I formed and initiated a plan.  I grunted and made a choking sound, which was all the more realistic because he'd just pulled a length of metal hard against my windpipe; I \emph{did} want to grunt and I \emph{did }choke.  Then I went limp and had every bug in the area cease moving.  Like snowflakes, the flies began drifting down from the air.



He let go of my hair, and my mask clacked hard against the floor.  I heard a girl scream, heard noises and shouts from everyone else.



I swallowed, partially to check that my throat really \emph{hadn't} been cut.  My costume had saved me.  I wished the gathered onlookers hadn't witnessed the scene.  It would have been better if the bugs had blocked their line of sight, as their noises of fear and alarm were going to get his attention.



I just needed a second to \emph{think}.  Mannequin could press an assault indefinitely, until he \emph{succeeded }in cutting my throat open or delivering that mortal wound.  It was like sparring against Brian, but worse in every way.  Mannequin was stronger, faster, he had more reach, he didn't get tired, he was \emph{good }and he was out to kill me.  He was versatile in a way no ordinary human could be.  He couldn't be caught in an arm-lock- his limb would just come free or bend in some screwed up way.



He could sense me somehow.  \emph{How}?  It had been reckless of me to assume that he used sight to get by, especially when he didn't have eyeholes in his mask.  The fact that he hadn't noticed I was faking meant he wasn't relying on sight, or his sight was limited enough that he couldn't make out the lack of blood through the cloud of bugs around us.  If he wasn't hearing my breathing, I doubted he had super hearing either.



Did he use radar, like Cricket?  It would be my first assumption, except my bugs hadn't heard anything of the sort.



No.  This line of thinking wasn't accomplishing anything.



I heard him sharpening his blades against one another with the sound of steel on steel.  I could sense the movement, from the bugs that were drifting down onto him.  A man in the crowd whimpered, and Mannequin turned towards him.



The metal singing in the pauses between the scrapes of blade on blade.  Mannequin was standing still, observing.



I had to come up with a plan of attack, or others would pay the price.  My deadline was the point, I suspected, that someone lost their nerve and tried to run.



If I was going to attack, I needed to find a weak point.  But he was \emph{smart}.  Before the disaster that had turned him into this, he had been on the brink of solving many of the world's crises.  Overpopulation, renewable energy, effective recycling, world hunger.  Even with tinker abilities offering the means, it took someone special to manage that and actually make\emph{ progress}.



It was a given that he wouldn't have any blatant weaknesses.  Any measure he didn't think of himself, he would have shored up by now, by virtue of being a longstanding member of the Nine.  He'd fought heroes and villains better than me, and he'd learned and improved in the process.



In that respect, perhaps, he and I weren't so different.  I'd developed in much the same ways.  The difference was that he had years more experience.  That, and he was batshit insane.



What would I do in his shoes, with his power?



I wouldn't leave any vital openings uncovered.  That was a given.  My focus -Mannequin's focus- would be on designing way to make himself a completely closed system.  It wasn't just sensible, it was the whole point of his transformation.  He'd have perfect recycling of all waste, dissipation of excess energy by diverting it to mechanical movement, intake of energy by absorption of heat.



Could that be a clue as to how he sensed the world around him?  Heat?  Or was it something completely different?  Radiation?  Radio waves?  Electromagnetics?



Putting myself in his shoes, I had to think of his motivation.  Why \emph{this} form?  I'd make myself resemble a doll or a store mannequin because\ldots it was an eternal reminder.  Didn't his wife and kids die when the Simurgh attacked?  There was a story there.



But what else?  Why resemble a \emph{human}?



To mislead?  Maybe the configuration of `my' organs and parts wasn't human in the slightest.  I might have gone the Aegis route and built-in redundancies for everything I could spare.  I wouldn't need a heart, kidneys, or a conventional digestive system, bone marrow or any of that stuff.  Everything I could strip away would be more room for equipment, more room for all the pieces and parts that help turn `my' individual body parts into perpetually self-sustaining systems.



His torso was the biggest section of his body.  It wouldn't have his heart, lungs or any of that, because he didn't have a circulatory system.  More likely, it contained his brain, his sensory organs/system, and whatever mechanism he was using to remotely control his arms, legs, hands and feet.  Unless he didn't want to put all his items in one basket.  It was easily possible for some of that stuff to be in his thighs and forearms.



If I were him\ldots I would have spent \emph{hours} carefully balancing the `ecosystems' of each individual part of my body.  Something that exacting and that fine tuned would be sensitive, fragile.  They'd be resistant to impacts, I wouldn't go around getting into fights if they weren't.  But heat and cold?  A crack in that exterior of his?  It could wreak havoc.



Okay.  I was getting a sense of him, maybe.  That said, none of that mattered if I couldn't hurt him in the first place.  Maybe I was thinking about this all wrong.



Bugs dealt with threats that were encased in hard shells all the time, didn't they?  They dealt with other species of bugs.  There were a hundred solutions there, if I was willing to look for them.



That was the spark of inspiration I needed.  In a matter of seconds, I had a plan.



It wasn't a good plan, but it was something.  As a just-in-case measure, I could try some other smaller plans, on the off chance that they might distract or even work.  Having those options, if nothing else, would make me feel better.  Mannequin had just brutally and unquestionably kicked my ass in the span of fifteen seconds, and it was going to be at least two minutes until I could even\emph{ begin} my plan, judging by how long it had taken my bugs to deliver the supplies from my lair.



The same instant I had that thought, I started everything in motion.  Every flying insect near my lair headed indoors to gather what I needed.



I made a mental note to make a more easily accessible opening to my lair, so I could do this faster in the future.



I made \emph{another} mental note to set up a clock with ticking hands, so I could have bugs ride the three hands and have a precise way of tracking time when I was in my territory.  I supposed it would have to be an old-fashioned clock, since Shatterbird had screwed up everything else.



I had to guess.  Roughly two minutes until I could start my plan.



As I lay face down on the floor of the factory, I tried to control my breathing so he wouldn't notice I was still alive.  The beat of my heart in my chest was so intense I was worried it would give me away.



Staying still was one of the hardest things I'd ever had to do, and I had done some hard things before.  Knowing that he might leap for someone and end their life any moment, it had me on edge.  Every second I could buy here counted because every second I \emph{didn't} have to fight him was crucial.



``Mommy,'' the word was drawn out.  Had to have come from someone young.  A toddler?  ``I don't want to be here!''



The rhythm of steel rasping against steel ceased.  Mannequin went still.



\emph{Shit.  }So much for my reprieve.



I pulled myself to my feet and stirred all of the bugs in the area into action.  They rose from the floor like a dark whirlwind.  I sheathed my knife and gripped my baton in both hands.



``Mannequin!''



He stopped and turned his upper body to face me.  His head cocked to one side.



``Yeah,'' I said.  ``You didn't get me.''



He turned back around and started walking toward the mother and the little boy.  The pair were huddled between an empty metal frame and a workbench.



``Hey!'' I shouted.  ``Come on!  Fight me!  Don't you have the balls to take on a teenage girl?  Or are they one of the things you cut away!?''



He didn't slow or hesitate at my words.



``Bastard!''  I ran for him.  It was a hundred percent possible he was baiting me, forcing me into a situation where I had to do something stupid or let the mom and the little kid get hurt.  Maybe if I'd been a harder person, I could have let him hurt them, knowing it was smarter in the long run.  But I wasn't capable of doing that.



What could I even do?  I had to make the call in the three or four seconds it took me to cross the floor of the factory.  He was more than half-again as tall as I was, and my weapons couldn't do anything to him.



I threw myself at the backs of his legs, colliding with the back of his knees and his calves.  Not all of his precarious balance was an act.  He teetered and collapsed backward onto the floor, his legs on top of me.



``Go!'' I screamed at the mother.  ``Run!''



She did.  Mannequin reached out to extend a blade into the back of her leg, and she fell, but someone else hurried forward to help her.



Mannequin's left leg snaked around my throat in an impromptu headlock.  I tried to slip out, to force his leg apart.  Even though I could move it, I couldn't squeeze my head through the gap.



Not counting the time I'd spent lying on the ground, buying time, how long had I lasted?  Less than thirty seconds?



Four blades sprung from the calf of his right leg.  He extended it high above me, and they began to rotate, slowly at first, then faster, like the blades of a fan.  Or a food processor.



He had me in a headlock, but the rest of me was free to move.  Gripping my baton with both hands, I swung it into the whirling blades with as much strength as my leverage afforded me.



My baton went flying out of my grip, but the blades stopped.  My heart sank as I saw them begin to rotate again, slowly.



They didn't return to the same blurring speed they'd been at before.  A few seconds passed, and they retracted back into his leg.



I might have been relieved, but I was still in his grip.



He heaved me upward, positioning himself with two hands and one leg on the ground, the other leg holding me up high.  My toes scrabbled to touch ground and fell short.  The grip on my neck wasn't perfect: it wasn't cutting off my blood flow, it barely impacted my breathing, but it still hurt, and my neck strained with the weight of the rest of my body.



I drew my knife and gripped the handle.  Then I drove it at my throat.  Or at Mannequin's leg, which was folded around my throat.  Same idea.  I aimed at the ball joint, striking a mere two or so inches from my own face.  Once, twice, three times.



I was swinging for a fourth hit when he shifted positions.  I couldn't be sure if he had hoped to gradually strangle me, to leave me dangling until I started begging or if he'd been poised for something else, but he'd apparently changed his mind.  He turned over, his leg unfolding from my throat at the same instant one large hand closed over my face.



He whipped me around himself in one tight circle, then let his arm go free from the socket, the whirring sound of chain feeding out swiftly becoming distant as I hurtled across the room.



I crashed into a pile of wooden boards that were riddled with nails and screws.  The metal points jabbed at me but didn't penetrate my costume.  I tried to get my feet under me, but the boards only slid underfoot.  His hand was still attached to my face.



He began to pull me forward, no doubt to repeat the process.  Half blind under the grip of his hand, I reacted in a heartbeat, slamming the point of the knife into the gap between his hand and my face.



Tattletale had said it was strong enough to serve as a crowbar.  I was glad to discover she was right.  Between the pull of the retracting chain and the leverage of the knife, I freed myself from his grip, his fingertips scraping hard against my scalp.  Flying back to him, his arm clicked back into place.  I tried to blink a blurry spot out of my vision, only to realize I had a scratch on the right lens of my mask where I'd hit it with the knife's edge.



The pain from being thrown around was belatedly making itself known.  Bruises, I could deal with.  Just so long as my body moved where and when I needed it to.  I felt the dull ache of a building headache.  From where I'd been gripped in the headlock?



Okay.  Still in one piece, more or less.  How much time had I bought?  One minute?  One and a half?  Could I hold out for long enough?  Could the bystanders?  The moment my bugs arrived would be the moment I could \emph{begin} my plan.  I'd still have to survive after that, and there was no guarantee it would work.  In fact, my gut was telling me it was a long shot.



Thirty seconds to a minute.  I was panting for breath, counting every second that he silently stared at me as something I should value.



What was going on behind that expressionless mask?  Was he coming up with a battle plan?  Maybe, maybe not.  He didn't really need one.  It could be that he was calculating how best to destroy me: not just killing me, but \emph{ruining} me.  There were enough ways he could do it.  Inflicting lifelong scars and injury.  Or he could go down the opposite road and murder the civilians, leaving me as the only one standing.  Both were very real possibilities, both devastating in their own way.



Or maybe, behind that hard shell, he was in the throes of mental anguish.  Maybe he was spending every second of every day reliving the day he lost his family and his dreams to a nigh-unstoppable, malignant force.



There was nothing I could do about his past.  Whoever he had been before, he was a monster \emph{now.}  I had to pull out all the stops to try and stop him from hurting anyone else.



It was time to enact battle plan number one, one of the two ideas I had in mind that almost definitely wouldn't work.  I set my swarm on him.  Up to this point, I had kept them largely at bay, using only the bare minimum necessary to keep track of my surroundings.  Now I smothered him, piling them on every available surface.



It didn't accomplish a thing, of course.  He started running toward me, weapons at the ready.  He wasn't impeded in his movements, nor were his senses -sight or otherwise- impaired.



I ducked beneath his first swing as he closed in, but I couldn't avoid the follow-up hit.  His second swing scraped off the armor on my shoulder and struck my chest.  Beyond the momentary pain, I was almost grateful for it, because the strike knocked me further out of his reach.



Some of my bugs managed to squeeze inside the slots where his weapons had emerged.  The spaces didn't perfectly match the bases of the blades, and the bugs were small.  There was nothing organic inside the sheaths.  Even the interior was completely sealed off.  Still, I managed to get bugs into the mechanisms, lodging their bodies inside the finer workings or killing one another to spill ichor and their bodily contents onto anything that felt sensitive.



Mannequin stepped back, and I watched as he retracted all of his blades, the slots they'd speared out of sealing closed behind them.  A wave of pressure and heat killed off every bug and likely most of the gunk I'd managed to smear inside.



Yeah, I hadn't figured that would work.  Plan one down.



For plan two, I needed my baton.  I could only hope it was in one piece.  I used my power and my eyes to search the factory floor, while keeping my head still, so he couldn't see what I was doing.



My bugs were almost here, arriving in droves.



I found my baton lying against the wall near where I'd been pinned by Mannequin.  I'd have to get by him to get it.



\emph{Fetch}.  I ordered my bugs, as Mannequin lunged for me again.  I didn't have a second thought to spare as far as telling them \emph{how}.  For now, I needed to survive.



This time, his attack was frenzied.  If I didn't know better, I'd have thought he was irritated.  I hopped back out of reach of the first swing, then quickly backed up as he followed that up with a series of rapid rotations of his upper body, momentarily becoming a blender-whir of whirling blades.



I was so busy trying not to get hit by the blades that I missed it when he tilted.  He balanced on one leg and kicked out wide with the other, letting the chain out so it could stretch the seven or eight feet to me.  I was knocked back onto the wood pile a second time, landing on the edge and falling to the ground a second later.



He stopped spinning and retracted his leg, apparently unfazed after the dizzying act of spinning like a top.  I saw my bugs tugging the baton, but Mannequin spotted them at the same time.  He stepped back and placed one foot on top of it.  With a kick, he sent it sliding across the floor, away from me.



\emph{Fuck.}  I'd have to take the slightly less efficient route.  I grabbed a stout two-by-four as I stood.  It was old, dusty, damaged by years of exposure, and the screws that clustered in one end were rusted.



Better than nothing, as weapons went.



His blades made that rasping sound as he sharpened them against one another, one edge of each blade, then the other.  After doing it \emph{just} long enough to lull me into a false sense of security, he lunged, blades spearing for my chest and throat.  I struck out simultaneously with the piece of wood.  It seemed to catch him off guard.  I struck too soon to hit him, but \emph{he} wasn't my target.



I clubbed at the uppermost blade, driving it down toward the floor.  I tried to avoid the edge and strike the flat of the blade, but my strike wasn't spot on.  I didn't see if I'd had any of the desired effect, because he collided with me, both blades striking the armor of my chest.  Pain exploded in my collarbone and ribs, but I didn't experience any of the telltale pain of impalement.  My armor had saved me.



Finding the tips stuck in the denser material of my armor, he whipped both arms to one side, throwing me a solid ten or twelve feet.  I sprawled where I landed.



I huffed out a breath, feeling pain in my chest with every movement.  Then I smiled a little.



My swarm had finally arrived.



The bugs flowed into the room as a singular mass and roughly half of them swept over Mannequin.  He wobbled a little, then turned his attention to me, uncaring.



Which was a good thing.  It was better that he didn't pay much attention.



Behind him, the bugs moved in an almost kaleidoscopic pattern, slowly expanding outward from a center point, their arrangement symmetric.



He paused and looked over his shoulder at the swarm.



He was apparently able to sense my bugs on the floor, floating in the air.  That much was apparent.  He hadn't, at the same time, been able to tell I \emph{wasn't} bleeding out into a pool on the ground, or that I was still breathing while I lay prone on the factory floor.  My plan hinged on two things; whether his peculiar means of sensing things would let him grasp what I was doing here, and if he would be able to do something about it.



The formation ceased expanding, then swept over him again.  Once again, he wobbled, staggered a step.



He charged through the mass of bugs that now sat between the two of us, running towards me.  I managed to parry one swing of his blade with my piece of wood, then jump out of the way of the second blade.  When I tried to block his kick with the two-by-four, however, I lost my grip and it fell to the ground.  He kicked me a second time, hard, and I staggered back, hand to my stomach, nausea building up in my throat.  I controlled my breathing to keep my dinner down.



Third pass with my swarm.  They focused on his legs, and very nearly unbalanced him.



I could see him pause, watched his head tilt quizzically.  I bit my lip.



To his right, my left, the swarm had once again gathered in a tight cluster, and were expanding slowly, with controlled movements.



The swarm consisted of pairings of flying insect and arachnid.  Every spider from my lair was clutching a bee, a wasp or a larger dragonfly, who clutched the spider in turn.  A thousand pairs.



Connecting to one another, these bugs quickly drew out five hundred or more lines of webbing.  Mostly dragline silk, this `net' maintained enough of the sticky webbing to attach to him, draping over his artificial body and \emph{staying} there.



I hadn't used the black widow spiders I'd brought into the factory earlier out of a fear that he'd realize what I was doing and counteract it before I could really get the ball rolling.  Now I gathered them up and brought them into play.  I used all of the spiders I'd already placed on him, focusing on his joints, reinforcing the stronger webs that were already there.  Their silk was nothing compared to the black widows, but it was \emph{something}.



He moved without a problem, either unaware or uncaring.  Silk strands stretched and snapped as he extended his arms, more broke free as he walked.  Alone, the threads were negligible.  It was together that they were stronger.  Much like my costume.



He tried to retract the blade in his right arm, but it caught.  Pressing the point against the ground, he bent it back into alignment.  It retracted on his next attempt.  My strike with the two-by-four hadn't done much there.  My second just-in-case measure hadn't worked out.



That same arm disconnected and extended towards me as he tried to grab for me, and I turned to one side just in time to avoid being caught.  He fired the other arm out with an almost explosive force and I managed to catch hold of it before it got a grip on my costume.



My swarm made a fourth pass, focusing on the chain of his extended arm and the joints of his shoulders, elbows, crotch and knees where the webbing had already accumulated to some degree.  Fifty or sixty spiders stayed on the extended chain, spitting out large amounts of their stickiest webbing.



He was trying to maneuver the arm I was holding to grab onto me, his fingers and wrist bending at unnatural angles as he sought a grip on my hands and wrists.  He changed tactics, making the blades in the arm spear out at random, to make it as impossible to hold as he could.  When \emph{that} failed, he whipped the chain.  I let go of the hand just in time to avoid being caught by the tail end of the whiplash.  He reeled it in, and it got about three-quarters of the way in before he ran into a slight snag.



The last quarter of the retraction process was a fraction slower.  Silk glue gumming up the works, I could hope.  I saw him look at his arm, then flex the fingers, as if to test them.



While he was distracted, I made a fifth pass with my formation.  I tried to be more subtle about it, carefully draping the silk over him rather than letting it pull tight against him with enough collective force to move him off-balance.



He attacked, stretching out the arm I hadn't gummed up.  The pain from the most recent hit to my stomach slowed me down, and his fist collided with me, knocking me over for what seemed like the hundredth time.  I managed to backhand it off of me before he could do anything, and hurried to my feet.



While the arm was still partially extended, I managed to deposit spiders on the chain.  They immediately began straining to produce silk glue on and around the mechanisms that allowed the chain to retract.  One spider wasn't much, but all together, it added up.



I could pinpoint the moment he realized what I was doing.  Extending the chain, he flung it across the room, the blade cutting a wide swathe.  I ducked clear, but two bystanders were struck down, screaming.  When he moved to retract that chain, the mechanism stalled.



His body was like Armsmaster's powersuit, but every piece of equipment he added necessitated that he cut away a pound of flesh.  I was inclined to suspect that, crazy as he was, that reality made him more inclined to go for elegant, efficient design over more rugged craftsmanship.  The propeller blades in his ankle, the chain retraction mechanisms in his arms, they were built to be lightweight, to use minimal energy, and achieve maximum effect at the same time.



He tilted his head, looking at the arm that was stubbornly refusing to retract back into place.



I made my sixth sweep with my bugs.  As the swarm passed, his head snapped up, looking at me.  As much as he could without eyes, anyways.  He knew what was happening.



A better cape than I might have had a quip there, an insult.  I hurt in too many places, in my ribs, my stomach, my shoulders, neck, back and legs.  Some of the pain was fierce, like a red-hot poker being driven with a constant, ceaseless pressure into the body parts in question.  I couldn't spare the breath.



The chain dropped from his elbow socket, and I watched as he paced over to his fallen arm, picked it up, tore the remaining chain out, and clicked it into place.



``Come on,'' I muttered under my breath.



Blades speared out of slots all over his body, some of which I hadn't even guessed were present.  Then he began spinning furiously, every body part rotating the individual blades with enough force that webs were cut before they could be secured in place.



Different tactic.  This time, the swarm took its time passing over him, thirty or forty spiders working at a time, their work relentless, ceaseless.  Each spider cut the threads so they drifted down like strings in the wind.



Falling gently instead of being stretched taut, they would drape over the spinning blades, attach to other trailing silk, and form a looser cloud.



I'd anticipated this.



The part where I was caught off guard was when he changed tactics, going after the civilians for the second time.



``Hey!'' I shouted after him.



I'd hoped to be more subtle about my second phase of attack.



Half of the swarm I'd brought from my lair was still waiting for the instruction.  I deployed them while running after Mannequin, stopping at the wood pile to get another two-by-four.



Someone screamed as Mannequin started cutting into them.  Two or three people, cornered by the monster.  One already in harm's way.



``Fucker!  Stop!''  I shouted, my words useless.



I moved on to the second phase of my attack.  As I'd done with the pens, markers, the candles and the bottles of disinfectant, I'd instructed my bugs to arrive with supplies in hand.



Some carried the scraps of silk cloth from my work on the costumes: The masks I'd made as trial runs, the belts and straps.  As with the silk that drifted in the air, they were caught by the blades rather than being cut.  Mannequin soon had a dark blur whirling around his upper body.



Other bugs packed the remainder of my costume design supplies.  Tubes of paint were rigid enough to be cut by the blades, creating small, wet, colorful explosions.  A large bottle of glue made its way to my hand, and I hurried to tear off the lid before a large group of bugs carted it off to him, holding it upside-down over his head so streams of the stuff could spill onto his head and shoulders.  Packages of dye were torn in half by his blades, expanding into clouds of black, brown, gray and lavender powder, sticking to any liquid on him, filling every gap to highlight the hidden slots for his weaponry and the seams where everything fit together.



Swinging underhand, I brought the two-by-four up toward the widest part of the buzzsaw whirl that was Mannequin.  Through luck as much as intent, I managed a glancing blow on the end of the blade, knocking it up toward the ceiling.  The momentum of his rotation managed the rest.  He tipped and crashed onto his side, literally falling apart in the process.  Lengths of chain connected everything, but nothing was in the right socket.  Some sort of built-in defense mechanism against heavy impacts?



My swarm flooded over him to draw out more lines of silk and to spill glue -both organic glue from my spiders and brand name supplies- where possible.



He began to reel the various parts in, slowly.  I hurried in to grab the one arm he'd disconnected from the chain and hurled it away.  Then I seized his head.



I knew he wouldn't have anything particularly valuable in his head.  It was too obvious a target.  But it was easy to get my hands on, it wasn't connected to too many other things, and there was a chance he might want to keep it.



Holding the head, I hauled back, pulling more chain from the neck.  With one hard pull, I hauled half of his body in my direction, the exertion making every injury I had screaming in protest.  Another pull, and I dragged his body another half-foot back, but I got one or two feet of length from the neck-chain.



Even with stuff gumming up the works, his chest clearly had stronger mechanisms inside it than the rest of his body did.  The chain began slowly retracting.



Someone appeared behind me, and his hands gripped the chain, just a bit behind my own.  He added his strength to mine, and Mannequin's body was dragged another two or three feet back.



``Where?'' he asked.  It was a burly bystander with a thick black beard, thick rimmed glasses and a red and black striped t-shirt.  One of my people.



I turned and let go to point.  There was a metal frame that had once stood around some equipment.  Now it stood empty, just a connection of metal bars.



``Stand back,'' he said.  I let go and backed off.  Without me in the way, the bystander was able to haul Mannequin another four or five feet towards the frame.  Another haul, and they were close enough to the frame.



I hurried forward, gripping the head, and winding it through and beneath the bars, tying it in the crudest of knots and tangling it in the bars in the process.  It dangled, the stump facing the ceiling.  Fifteen feet of chain trailed between it and Mannequin's body.



Mannequin had only just managed to reel in the chain and reconnect his remaining arm, and was using it to attach his legs securely into place.



I had only seconds.



Having my bugs in the area, I knew exactly where to find what I was looking for.  I hurried over to the corner and hefted a cinder block.



I wasn't halfway back to the head when I saw Mannequin stand.  I abandoned my plan, dropped the block and stepped away, circling him, putting distance between myself and his head.  His attention seemed to be on me.



Had I pissed him off?



He wasn't spinning any more, and I could see the damage the bugs had wrought.  Dense webs and scraps of cloth had collected across his body, and only half of the blades had succeeded in retracting in the face of the silk, glue and other gunk.  Color streaked him, both liquid from the paints and powder from the dyes.



I gathered my bugs into another formation.  We were running low on silk, but I'd have to deal.



He stepped forward, and his movements were more awkward than usual.  Good.  That might mean the ball joints weren't in pristine condition anymore.



He moved again, disconnecting the chain to free himself from the metal frame I'd tied the neck-chain to.  He wasn't focusing on me.  I felt out with my bugs and sought his target.



His arm.  It crawled weakly for him, using the fingertips to scrape forward.



The moment I realized what he was after, I redirected a portion of my web-spinning swarm to the hand.  Then I limped to my left to put myself between him and his target.  My swarm passed over him.  The seventh strafing run.  He slashed at it as it passed in a surprising display of emotion.



He reached into the hole where his neck and head were supposed to be and withdrew a small knife.



I adjusted my posture.  He was a tinker, and that knife could be \emph{anything}.



He pressed a switch, and it was soon surrounded with a gray blur.  I recognized it as Armsmaster's tech.



A weapon with that exact same visual effect had done horrendous damage to \emph{Leviathan}.



He stepped forward, and I stepped back.  Behind me, the arm jumped.  Mannequin was using the telescoping blade to help push it in the right direction.  It was trying to take a circuitous route around me.



My bugs made their eighth sweep past the headless Mannequin.



He lunged for me once again.  This time, there was no blocking the hit, no letting my armor absorb it.  His movements were ungainly, unbalanced by his lack of an arm, but he stood nine feet tall, usually, and that meant he had \emph{reach}, no matter the type of weapon he was wielding.



I backed off, rapidly stepping away, all too aware that my spiders weren't working fast enough to stop him before he landed a hit.  I was swiftly running out of room to retreat.



There was a sound, a heavy impact followed by the noise of ringing metal.  Mannequin stopped and whirled on the spot, striding back the way he'd come.



The sound came again.  I chased, trying not to limp, knowing there was little I could do to stop the monster.  I crossed half the factory floor before I saw what had earned Mannequin's attention.



The man who'd helped me with Mannequin had the concrete block in his hand, and for the third time, be brought it down on Mannequin's head.  The head came free of the chain and fell to the ground, rolling briefly.



The man hefted the cinder block again, saw Mannequin approaching, and changed his mind.  He dropped the block onto the head and then ran.



Mannequin didn't give chase to his attacker.  Instead, he stooped down to pick up his head, then stood straight.  I stopped where I was.



For long moments, Mannequin held the head at arm's length.  Then it fell to the ground.



Seconds stretched on as his arm flopped its way towards him.  My spiders swarmed it, surrounding it in silk.  Only the blade was really allowing it to move, now, the fingers struggling around the silk to move it into position for the next sudden thrust of the blade.



Mannequin turned his attention to his arm, and I set my swarm on it.  A thousand threads of silk, each held by as many flying insects as I could grip it with, all carrying the arm aloft.  I brought it up to the ceiling, and began fixing it in place, building a cocoon around it.  My enemy turned his attention to me, his shoulders facing me square-on.  As he no longer had a head, I found his body language doubly hard to read.  Had I irritated him, doing that?



He stepped forward, as if to lunge, and the silk that wreathed him hampered his full range of movement.  His leg didn't move as far as he intended, and his missing arm displaced his sense of balance.  He collapsed.



``Want to keep going?'' I asked his fallen form, my heart in my throat.  I stood ready to jump and react at a moment's notice.



Slowly, he pulled himself to his feet again.  Twice, he used the knife to slash at the silk.  On the second attempt, I hit him with the formation of bugs for an eighth sweep of the silk net, hoping to throw him off-balance enough that he'd stab himself.  No such luck.



Standing straight, Mannequin shifted his grip on his knife and then raised one finger.  Wagged it left and right, that same gesture of disapproval, condemnation.



Then he turned to leave, striding for the door.  I didn't try to stop him.  I didn't have it in me.



I watched him leave with my bugs.  Felt him get three, four, then five blocks away with my power, before he was out of my range.  The second he was gone, all the strength went out of my legs.  I collapsed onto my knees in the center of the room.



I hurt all over.  If Mannequin hadn't broken something in my ribs or collarbone, he'd fractured something.  But pain was only part of it.  Physically, I was exhausted.  Emotionally?  Doubly so.



Charlotte appeared at my side and offered me a hand.  The murmurs of conversation started to sound around me.  I tuned it out.  I couldn't take the criticism, and I didn't deserve any praise.  How many people had been hurt while I fought Mannequin?  How many people had died because I hadn't been on the alert?



With Charlotte's help, I stood.  I shook my head at her offer for support standing.  Moving slowly and carefully, not wanting to embarrass myself, I walked over to the dismembered head.



It was miniscule, but there was a drop of black fluid beading at the seam in the neck where the chain had been threaded.  Apparently that was enough of a flaw for Mannequin to abandon it.  I left it where it was.



Then I hobbled over to the body of the gray-haired doctor.  Getting onto my knees was painful, but I did.  I gently turned her head and stared into her open eyes.  Light blue, surprised.



``I'm sorry,'' I told her.



I couldn't think of anything more to add or say.  A minute or two passed before I gave up on it.  I left her eyes open; using my fingertips to close her eyes seemed presumptuous and trite.



I cut the threads with my bugs and let the arm fall from the ceiling.  More than one person was startled at the sudden drop and impact.



``Throw the head and the arm into the ocean,'' I said, to nobody in particular.  ``If you can find a boat, drop it somewhere deep.''



``Okay,'' Charlotte said, her voice quiet.



``I'm going to go.  I'll be using my bugs to watch for more trouble,'' I said, as I began limping toward the door.



I'd won.  So to speak.





