





I hadn't actually slept in for a long, long time.  It was not the start I wanted for my day.



I'd been too tired to sleep, I hadn't been able to get my thoughts to slow down, and I hadn't been able to resist just\emph{ one more} check of my territory to ensure people were safe and sound.  Compounding it all were my injuries, which did an excellent job of jolting me from the twilight of almost-sleep any time I moved the wrong way or shifted position.  When daylight had started to stream in through the slits in the metal shutters, I'd pulled a pillow over my head and tried to get just a few hours more.



If I wound up having to face down Mannequin or any other members of the Nine, I'd need to be well rested.  Running on two or three hours of sleep would get me killed.



It sure didn't \emph{feel} like the added sleep I got made any difference.



My injuries and the general aches from running barefoot and fighting Mannequin had all melded together into one giant, stiff bruise.  It would be easier to name the parts of me that \emph{didn't} hurt.  My chest was the worst, each of my breaths drawing a stab of pain from the lowermost ribs of the right side of my body.  It took me two tries to get up from my bed and stand.



A quick investigation showed that bruises had spread across my abdomen, yellow and blue.  Some careful prodding showed that the tissues beneath the bruises weren't rigid or particularly tender.  That meant there was no serious internal bleeding, if I was remembering right.



If this kept up, I was going to need another go at the first aid courses, to refresh my memory on the particulars and brush up on my skills.  February felt so very long ago.  So much had happened in the last few months.



Shuffling over to my bathroom, I groaned quietly at the sight of the shards of mirror and shower door that were carpeting the floor.  I made my way back to my room and put on some slippers, grabbed a shirt I didn't care much about and dropped it on the bathroom floor.  I kicked it around enough to get the worst of the shards out of the way, brushed the glass out of the shower and onto the tiled floor, and then cranked the shower on.  The water pressure wasn't even half of what it should be, and it was \emph{cold}.  It didn't warm up over the thirty seconds I stood there holding my hand under the flow.



I jumped in anyways, in the hopes of waking myself up and getting my hair wet enough that I could make myself look \emph{somewhat} presentable.  I knew from experience that not washing my hair had a way of making it frizz out hardcore.  Not that I'd be able to tell, with every mirror within a thousand miles in pieces.



I dried off, put on my contacts, combed my dripping-wet hair into place, and stepped back into my slippers to navigate through the sea of glass shards and head back to my bedroom to dress.



My TV, laptop and phone were all useless.  There was no way to get information on recent events.  I couldn't call the others, couldn't check the news for details on the events of the past night, couldn't even know if I'd managed to save anyone when I'd been waking them and leaving messages.  I was left to expect the worst, and it soured my already iffy mood.



I made my way downstairs, unlocking the door that led between the second and third floors.  The second floor was relatively unscathed – the metal shutter had kept the floor-to-ceiling windows from sending their contents indoors, and the terrariums were hard plastic rather than glass.  Knowing Shatterbird was in town, I'd been reluctant to spend much time in a room with sixty or seventy sturdy glass cases, and I was glad to have one less room to clean.  Still, there was no shortage of mess.



Sierra and Charlotte were downstairs, talking at the kitchen counter.  They fell silent as I appeared.



They didn't speak as I walked over to the cupboard.  Tea.  Tea, maybe some toasted breakfast pitas, some bacon, an egg\ldots



Opening the cupboard, my hopes of having a solid breakfast to start my day were dashed. Bottles of spices that had been on the same shelf as the teabags had exploded, sending their contents and countless glass shards throughout the cupboard.  The cupboard reeked of cinnamon and cumin and various peppers.  They weren't the only casualties there.  Bottles of cooking supplies had exploded on the upper shelves, and their contents had settled overnight, most of it pooling on the shelves in layers of congealed liquid that were thick with the needle-thin particles of shattered glass.



I looked at the pair of them.  Neither spoke, and Charlotte even looked away.



I hated this.  Hated feeling flawed, knowing they saw me that way.  Being bruised, sore and stiff, I was visibly \emph{mortal }to them.  I hadn't been able to stop Mannequin from hurting bystanders, or protect and warn my people about Shatterbird.  How were they supposed to respect me as someone in charge?  Sierra was even older than I was.



Well, I'd have to make use of them anyways.  My focus on the cupboards and the damage inside, I asked, ``Charlotte, you up for a job?''



``Yeah,'' she said, behind me.  When I glanced back at her, she looked away again.  I knew I'd taken some hits, but did I look that bad?



``It's a bit of a walk, but I need to get up to date on events.  You'll be going to the territory of a guy named Regent.  He's a friend, and it's close.  Tell him about the Mannequin incident, tell him I'm alive, and get details on what happened to Tattletale and the father.''



``The father?''



``He should know what I mean.''



``Okay.''  She met my eyes as she responded.  Better.   I wrote the address down for her, then watched as she headed off to pull on her shoes and make her way off to the cellar exit.



``And me?'' Sierra asked.



``Go to the basement, get a box of supplies, and bring it up.  There should be a propane stove in there.  Cook up some rice, and then start cleaning out the cupboards.  Wear gloves, and focus on picking out the stuff we can keep from the stuff that needs to be thrown out.  Use the box from the supplies to hold some of the extra trash if you need to.''



``Okay.''



I walked over to the corner to find a broom and dustpan.



``You're cleaning up too?''



``Yeah.  You were at the hospital last night, right?  How did things go?''



``Nobody listened to me at first when I tried to warn them.  It was only when Battery showed up at the hospital and confirmed that the Slaughterhouse Nine were around that people started trying to prepare, but there wasn't a lot we could do in those ten minutes.  There were a lot of people in the hospital, and a lot of equipment, monitors and displays, lots of windows.  Everyone who could got under their beds, and people put mattresses against the windows in rooms where there were people who couldn't move.''



``But they were okay?''



``Most?'' Sierra frowned. ``I couldn't really tell.  It was chaotic, lots of people running around, equipment failing.  Battery tried to grab me to ask me how I knew what was happening, and I used the chaos to slip away, spent the rest of the night in my parent's room, hoping she wouldn't spot me.''



``And they're okay?  Your parents?''



``They're okay.''



I smiled a little.  ``Well, that's good.''



She smiled back.  ``You know, you're not what I expected.''



``I'm not what \emph{I }expected, frankly,'' I said.  I turned my attention back to the cabinet, found the dustpan and stood up.



``That reminds me--''  She paused.  ``Nevermind.''



``Say it.''



``It wasn't last night, but I overheard something at the hospital.  Something involving you and Armsmaster?''



I sighed, suddenly reminded of how weary I felt.  I saw her expression fall.  She said, ``I didn't mean to upset you.''



``No.  It's fine.  What did you hear?''



``That you betrayed your team, and that you'd wanted to be a hero but, um,'' she paused, ``Couldn't?''



She'd changed her mind about how she was going to finish speaking.  What had she left out, and had she stopped herself from saying it for my sake or for her own self-preservation, not wanting to piss off the villain?  \emph{I wanted to be a hero and I failed?}



Given recent events, I wasn't sure I could blame her for thinking along those lines.



``No, that's not exactly right,'' I responded.  ``Long story short, once upon a time, I wanted to be one of the good guys.''



``What happened?''



``Took me a while, but I decided I'd rather have the likes of Tattletale and Grue at my back instead of siding with the sort of people who follow Armsmaster.''



``Really, Armsmaster?  Is he that bad?''



``Bad enough that Mannequin wants him to be the ninth member of their group.''



Sierra's eyes widened.



I figured I wouldn't mention that two of my teammates, including the one I'd sent Charlotte to meet, had also been nominated.  Regent had only been nominated out of spite, and Bitch\ldots I wasn't sure what the story was there.  ``I'm going to be upstairs, cleaning up the balcony and the other rooms.  Give me a shout when the rice is done, or if you find anything breakfast-ish that's edible.''



``Okay.''



I headed up to my bathroom and began to sweep up.  I deployed bugs to help me find the shards that the broom wasn't catching.



I occupied myself with my other bugs as well.  I went out of my way to avoid using the spiders I'd employed to fight Mannequin, drawing from bugs in the streets and surrounding area instead.  I sent the weakest, smallest and most useless of the bugs to my spiders for a morning meal, then fed the non-spiders who were a \emph{little} less reliant on protein.  With the other nearby bugs, I started collecting the smallest pieces of glass throughout the house.



The uncertainties of the day, the worries about Lisa and Dad, having my routine disrupted and the spoiling of my breakfast and morning shower had put me in a bad mood.  It would have been nice to say that it made me feel better, getting things in order again, and it \emph{did}, but it wasn't a cure-all nor was it a perfect distraction.  There was no way I could relax with the things I had hanging over my head.



Doing this felt like I wasn't doing something to help Dinah.



Once I finished the bathroom, I tidied my room and opened the shutters on the windows.  Glass that had fallen against the shutter sloughed off to the second floor balcony, with stray shards falling onto the hardwood.  My bugs obligingly fetched them up for me.



Reams of glass shards fell as I opened the heavy shutters that stood just behind the pedestals with the mannequins I was using to design the costumes.  I stepped out onto the balcony and set about sweeping up the glass and dumping it into the trash can, using my bugs to collect what the dustpan wasn't catching.  I wasn't in costume, and I was in plain sight on the balcony, but I doubted the concentration of bugs was enough to draw attention.



Ten minutes passed before I heard from Sierra.  I assumed it would be about the food, but it wasn't.



``Skitter!  You've got company!''



Every bug I had in the cabinets and corners of the room streamed forth to check the intruder, my thoughts immediately shifting into a combat mode.  What escape routes did I have?  Could I help Sierra if there was trouble?  What tools and weapons did I have on hand?



The second my bugs settled on the intruder and felt that familiar emanation of outward pressure, like a faint breeze, I calmed down.  I felt a mite embarrassed as I made my way downstairs to greet Grue.



``Christ, T- Skitter!'' he exclaimed, the second he saw me.



``What?''



``Your, um--'' he gestured at Sierra shaking his hand, agitated.



``Employee?''  I suggested.



``Your \emph{employee} just informed me that you fought \emph{Mannequin }last night\emph{?}''



``Yeah.''



``Are you suicidal!?''



``He's not that strong,'' I said, defensively.  ``I mean, scary as fuck, he's \emph{strong}, but he was beatable.''



``Do you not recall the \emph{very} specific numbers we got on our chances against these guys?  \emph{Fifty-five} percent chance we die if we fight them!''



``There were people in danger.  \emph{My} people.  I thought a forty-five percent chance of survival was worth the risk.''



He tapped his finger against the forehead of his helmet.  I could almost make out the noise through the thin emanation of his power.  ``Could you ask your employee to give us some privacy?''



``I can go for a walk,'' Sierra said.



``Thank you,'' I told her, ``I'll signal you with my power when we're done.''



My heart was speeding up just a bit as we waited for her to leave.  I distracted myself by limping over to the propane stove that was positioned on the countertop and checking the rice.  There were containers and boxes of food arranged on the counter that Sierra had apparently checked and deemed edible.  Nothing especially good for breakfast.



As the door closed behind Sierra, I hugged my arms against my body and said, ``Please don't tell me you asked her to leave because you have bad news about Lisa or my dad.''



Grue pulled off his helmet and the darkness dissipated around his head.  It was Brian's frowning face I saw, now.  ``Your dad is fine.  He was already fully checked out and sent home.  Lisa is\ldots less fine.''



``Don't say that.''



``It's not life threatening.  I just don't know if it's hit her yet.  Coil's doctor stitched her up, but he told her to expect a scar.  I don't know if it's shock, the blood loss, or if it's that she hasn't seen herself in a mirror, but she doesn't seem to care.  Cracking jokes, even.  Isn't- is it sexist of me to wonder why a girl doesn't care more about her looks being spoiled?''



``It's easily possible she \emph{does} care,'' I said.  I was thinking back to her interactions with our enemies in fights.  In particular, our run-ins with Glory Girl and Panacea during the bank robbery and Jack Slash last night seemed to stand out.  ``I think maybe she handles stress and problems by throwing herself headlong against them.  It's how she operates in costume, against serious threats and unexpected situations.  There's a word I'm trying to pin down, it's not reckless, but--''



``I think reckless may be a very good word to choose,'' Brian replied.



``No.  It's\ldots'' I reached for the word and couldn't find it.  I was too tired, and my brain wasn't really in that gear.



``I'm surprised, sometimes, at how much attention you pay to us.  You seemed to have Rachel down cold, and your description of Lisa seems pretty apt.  Makes me wonder how you've analyzed me.''



``I'm not all that.  Really.  There are exceptions, but dealing with people isn't my thing,'' I said.  Feeling awkward, I distracted myself with the rice, taking it off the propane stove and scooping some out into a bowl.  Holding the pot, I pulled at the wrong muscle and felt my rib protest.  I winced, and I wasn't able to hide it.



Noting my pain, Brian commented, ``I can't help but worry you're self destructing, Taylor.  You can't go up against the Nine to protect people you don't even know.''



``I can.  I'll manage.''



``How much sleep did you get last night?''



``Dunno.  Two or three hours, but I slept in.  What time is it?''



``Nine.''



``Maybe four hours?''



``You're going to run yourself into the ground at this rate.  Or get yourself killed.  Take your time.  Go on the defensive, tell your people to stay out of trouble and avoid drawing the Nine's attention, \emph{rest}.  You can work on this territory thing over the next few \emph{weeks}, instead of \emph{days}.''



I shook my head, ``I can't.''



``Right.  Just like you rejected Hookwolf's suggestion that our groups take a break.  I won't say that hearing you muttering to yourself was the \emph{entire} reason I refused his offer, or even half the reason, but it was a factor, and I think I deserve answers for going up to bat for you.  What's going on?''



``I made a deal with Coil.''



Brian folded his arms, much as I was doing.  ``What deal?''



``He said that if I can prove my services are worth it, he'll release Dinah.''



Brian shook his head.  ``No.  There's got to be more to it.  You've been distant, driven, and you've done some very un-Taylor-like things in the past few weeks.''



I ate some of the plain brown rice.  Could I tell him?



``There is more to it.  Lisa and I talked it over after the Endbringer thing.  She doesn't like the Dinah situation either, even if she's more willing to roll with it.''



``Right.  Just for the record, I'm not in love with the kidnapping and confinement of some kid, either.''



I nodded.  ``So Lisa suggested the deal.  But knowing Coil, and from what Lisa says, and from the way Coil framed it when I posed the deal to him and just my gut, I- \emph{we} don't think he's going to let her go.''



``No, I don't think he would.  Her talents are too valuable for him.  But that doesn't explain your attitude lately.''



I shook my head.  ``I--''



I stopped and raised one hand.  Sierra was outside, not too far away, and there was a small group of people around her.  What had gotten my attention was the fact that she was tapping her finger against the origami cube.  She'd wanted to signal me without doing anything overt, maybe.  Or without my calling a swarm down to her location.



``--Something's going on outside.  Come with?''



Brian nodded.



I headed upstairs and got my costume on in record time.  I couldn't help but note how dusty it was from last night's encounter, and how the one arm was still crusty with old containment foam.  It was torture to actually get my limbs into the legs and sleeves and zip up, and to contort myself to attach my armor.  Especially doing it \emph{quickly.  }I ended up enlisting Brian's help with the armor at my shoulders and back.



I could feel Sierra's steady but insistent tapping on the cube all the while.



They were a short distance down the beach, but they started walking towards us a little bit after we entered the storm drain, and met us halfway.



Sierra was in the company of a pair of Japanese boys and a petite Chinese girl with a pierced nose and a thousand-yard stare.  There was a degree of attitude coming from them that was all too familiar.  Gang members.  Of course.  Just because Lung and Bakuda were no longer around didn't mean there wouldn't be scraps of the ABB in the area.  They wouldn't be \emph{liked}, but they were there, they were equipped for trouble and criminal activity was all they knew.



``Sorry to interrupt your business meeting,'' Sierra said, looking from me to Grue.



``It's fine.  What's going on here?''  I controlled the tone of my voice.  They didn't seem too fazed by this encounter with two supervillains.  Were they veterans of Lung's rule?  Or Bakuda's?



A Japanese guy with a mop of hair covering his eyes and a bad slouch looked from Sierra to me and spoke in a very American accent, ``You still looking for muscle?''



He didn't look like he had much muscle, but I wasn't about to comment on that.  If nothing else, I was a little too stunned at what he was offering to say anything witty.  ``Pretty much.''



``We heard you took on Mannequin,'' the girl said.  ``That's ballsy.''



``Thanks,'' I said, in my driest tone.  Stupid as it was, that statement \emph{meant} something to me.  Nobody had really congratulated me since my fight with Mannequin.  \emph{I} hadn't congratulated myself.  It was hard for me to wrap my head around the fact that they \emph{respected} me for what had happened with Mannequin.  A victory was a victory, but people had gotten hurt, \emph{I'd} gotten hurt.



The second Japanese guy spoke up.  He was in his early twenties and his accent was thick enough that I didn't realize he was speaking English at first.  He pronounced `girl' more like `gurru'. ``Other day, girl was knocking on neighbor's door, talking about you.  Said you was good boss.  Nice, generous, fair.  But we think that means you weak, before, not so much of that now.''



I shook my head slowly.  ``No.  I'm not weak.''



``We know you has trouble with Lung and ABB before.  Not friendly.  But they gone, we still here.''



``You should know this isn't about preying on the people in my territory.  Just the opposite.  If you're looking for an excuse to bully the people around here, you're in the wrong place.  The only people we fuck with are our \emph{enemies}.''



There were nods from all three.



``No starting violence, no drug dealing, no prostitution, no threatening people, and no drug use or drinking unless it's a hundred percent limited to your own time.''



A look passed between the two boys.  Which of my points had given them that momentary hesitation?  Still, they nodded again.



``Do you guys have a place?''



``Nah,'' said shaggy-hair.



``Come on,'' I said.



I led them to the nearest spot to get from the beach to the old Boardwalk, and into the Docks.



I had our destination in mind.  During my stay in the area, nobody had occupied it.  A thorough check of the structure found no splintering supports or framework, and there was no crumbling masonry.



I opened the doors and strode inside, followed by the new members and Sierra.  Grue followed at the tail end of our group.



The square building had been a garage for the biggest sorts of trucks or for boats, and sported three sliding metal garage doors, only one of which still opened.  A cargo container sat in the back corner.  I had my suspicions that boxes of recyclables had been piled up along the walls when Leviathan's wave hit.  Now, scraps of metal, paper and other trash littered the floor inside until the floor was barely visible.  ``If you're really interested in joining, you can start by cleaning this place up.''



``Why?'' the girl asked.



``If my say-so isn't good enough--''



``No,'' she raised her hands to stop me.  ``Just\ldots can't I know what the point is?''



``I want you somewhere accessible.  This is close to my command center, it's dry, it took a hit from a tidal wave and it's still in remarkably good shape, and it's spacious enough to serve our purposes.  At least to start off.''



``Can I ask what they are?''



I looked around, and it was Grue I looked at while I spoke.  ``Having everyone in the Docks spread out like this, over this wide an area?  It's a problem.  We've got single families living in warehouses and factories that could comfortably house three to five families, and they're dealing with problems that we could handle far more easily as a group.  And there's the logistics of it, getting supplies to everyone when there's only three to six groups of people on a given city block.  I want to bring people from the fringes in, so we're not so spread out.  Get everyone working for the collective good.  Build a community and tie everything to a smaller area.''



``There's going to be resistance,'' Grue spoke.  ``People aren't going to want to move, and they're too spooked about run-ins with Chosen and Merchants to trust one another.''



``If--'' Sierra started, but she stopped when Grue snapped his head around to face her, intimidated.  She tried again, ``If she's going to try it, now would be a good time.  Word's getting out.''



``About what, specifically?'' I asked.



``You fought Mannequin, you said you'd make him pay, and then you did.  And you did it to \emph{save }people, people from the docks.  I think people are realizing you're for real.''



I couldn't think of a response to that, and nobody volunteered anything further.  Instead, I said, ``Come on, let's get to work.''



It wasn't the nicest of jobs, but my new employees worked without complaint.  Or, to be more specific, the girl and shaggy-hair complained often but they didn't direct those complaints at me or the job, specifically.



Since the usual means of communication were out, and it might be some time before cell phone towers were out, I'd have to use messengers to pass word on to Coil.  I began explaining what I planned to do with the space to Sierra, outlining the need for bunk beds, a cafeteria or kitchen and an area for people to sit.  The area wasn't a quarter of the size of Lisa's shelter, but it was a refuge, maybe.  A place where people could congregate and get some peace.  And, ideally, it could be a barracks for my soldiers.



I instructed my new employees to stack the crates of trash outside the door.  I stayed outside with Sierra and Grue when they went back in to get more.



``You're going to have to watch those ones,'' Grue said.



``I know.  Listen, I want to send Sierra down to meet the boss, pass on word about stuff I need.  Can you escort her part of the way?''



``Sure,'' he said.



``If you're willing, Sierra?  I know it's somewhat dangerous to cross the city, and our groups don't control \emph{all} of the territory between here and there.  I could send one of those guys with you.  Bit of a walk, though.  Maybe forty-five minutes both ways.''



``No, I can go alone, if it's not too bad.''



``Good,''  I said.  I turned my head to see a trio of young men who were approaching us.



It took the one in the lead a bit of courage before he could approach me.



``Yes?'' I asked, when he didn't speak.



``We were remembering how some girl was saying you were recruiting, the other day.''



``I was and I am.''  My heart was pounding.  Why was this happening now, when it had met with only resistance earlier?



``Don't want to do anything illegal.''



``Not asking you to.  You okay with starting with some clean-up?''



He looked at his buddies -or were they brothers?- and nodded.



``Sierra here will tell you what needs to be done.  Put in a good effort and I'll pay you at the end of the day.''  My thoughts were on the small safe that I was using as a bedside table.



His eyes widened slightly at that.  ``Mind if I go and get my cousin?  He'll be interested too.''



``Go.''  I ordered, and Sierra led two of them inside while the leader of the newest group ran off at a half-jog.



``Seems like you started something,'' Grue said, when the last of them were out of earshot.



I shook my head.  ``I don't even understand how.''



``Still think you're moving too fast.  Like I said earlier, there's no good reason for it.''



``Dinah's a good enough reason for \emph{me}.''



``Maybe.  But you've got to find time to relax, get some sleep, maybe have some fun.  Or you're going to make mistakes, and you'll set yourself back days or weeks in your plan.  Slow and steady wins this race.''



``Can't afford slow and steady,'' I said.



``\emph{Why}?  You were telling me earlier, but we got interrupted.''



I'd been glad for the interruption, and I was profoundly disappointed the subject had come up again.  I folded my arms and looked away, down the road to where it gradually sloped to the shattered Boardwalk and the ocean beyond.



Here was the leap of faith.  The test of my trust in him.  ``Because if I don't amaze Coil, if I don't force his hand and give him absolutely no reason to say I failed\ldots he's going to keep Dinah.  If he does, the only way to free her is going to be if Tattletale and I take Coil down.  And I don't think we'd succeed.''





