





She couldn't shake the idea that it was a hoax.  Three times, she almost turned around and headed back home.



Twenty eight miles west from New York City, down the 202, to where there were more trees than houses and the roads hadn't been maintained for too many years.  It hadn't rained recently, but there were murky puddles in the road where the water had settled into broad depressions.



Water sprayed as she deliberately aimed for one puddle.  Forty five minutes of driving, trying to convince herself this was real, not seeing anyone on the road for the last ten minutes, she'd started to feel lost.  The concrete action of steering into the puddle and getting the expected result seemed to ground her.



Every action had an equal and opposite reaction.  It was the way things were supposed to work.  Action and consequence.



Driving to the middle of nowhere was the action.  But what was the consequence?  Wasting two hours of her time on one of the last weekends of freedom she had before she was due to start school?  For a mere \emph{chance} she might get what she needed?



She had to stop and reverse to reread a number on a mailbox.  2062.  She steered into the long dirt driveway.  A farm sat in the distance, with a rotted-out grain silo and a barn nearby.



What if this wasn't just meant to waste her time?  What if it was more sinister?  If there was a gang of men waiting for her, ready to drag her off somewhere\ldots



She shook her head.  She knew how to defend herself.  Her father had taught her, and she'd taken classes.  They didn't necessarily know she was a woman from her email address. She'd left a note with her roommate, sealed with instructions not to open it or read the details unless she failed to return home.  Topping it off, the necklace she wore had a built-in GPS.  A gift from her sixteenth birthday from her dad.  If there was trouble, the note she'd left with her roommate had instructions to contact her dad and track her down using the necklace.



She stopped by the barn and sat in the car for a minute, peering around to try to see if anyone was near, the engine idling.  A minute passed before she felt secure enough that she wouldn't be ambushed and shifted the car into park.  She held the key like a weapon as she stepped out of the car.  She didn't hold the individual keys between her fingers, like an amateur would be inclined to do, but held it like a knife instead.



The barn was the final destination of the route the email had outlined for her.  Empty.  It smelled of stale manure, rotting hay and mold.  The exterior was covered in peeling red paint.



She checked her watch.  She was eight minutes early.



There were no other cars on the property.  That meant there were eight minutes for someone to come down that road with the cracks, potholes and puddles, pull down the long driveway and come meet her at the barn.



Her weight shifted from foot to foot, as her impatience manifested in restlessness.  Eight minutes before she found out if she'd been played for a fool.



She used her shoes to kick a few loose stones from the dirt driveway, smoothed it out, and then kicked them off.  Barefoot, she planted her feet a shoulder width apart, then bent her knees as though she were sitting down in a chair, her arms outstretched in front of her for balance.  She bent low, straightened, then repeated the process several more times.



\emph{Deep breaths}.



Centering herself, she began on the next form, placing her feet perpendicular to one another, and transferring her weight from one foot to the other, from toe to heel to the heel of the other foot.



Her digital watch interrupted her exercises with a steady beeping.  She'd set an alarm for the meeting deadline.  Right this minute, she was supposed to be meeting someone.



And there was no car in sight.



Sighing, humiliated, she donned her shoes, opened her car door and prepared to leave.  She wouldn't speak of this to anyone.



``Leaving?  After coming all this way?''  The voice was female, rich with hints of a French accent, but the English was probably better than her own.



She turned, then stepped a few feet in front of her car to look inside the barn.



A woman stood there, dark-skinned, with her hair cut into a short style that was more utilitarian than stylish.  She wore a doctor's lab coat and held a white plastic clipboard with both hands.



That wasn't the startling thing.



At a point halfway inside the barn, there ceased to be any barn at all.  White tiled floor and white-painted walls stretched a distance behind the woman, and the ceiling was all glass, hiding a smooth distribution of fluorescent lights that made it all glow evenly.



``Who are you?''



``Some call me Mother, but that is meant to be tongue-in-cheek.  Those with a more professional attitude know me as Doctor.''



``I'm--''



``No names.  We've already investigated you, we know much of what we need to know, but I think there is a great deal of symbolic value in having you maintain some anonymity.  Pick a name, and I will use it for the duration of this meeting.  It doesn't need to be permanent or long-term.''



``Okay.  Is it supposed to be a fake regular name or a codename or\ldots?''



``Anything.''



``Jamie.''  It was the name her parents had been planning to give her baby sister.  They'd broken up before that happened.



``Jamie it is.  Come.  I have an employee that is relocating this section of my offices to this spot, but it taxes him, and there'll be less wait for the return trip if we don't strain him.''



Jamie looked over her shoulder at her car.  The GPS wouldn't do her much good here, she suspected.  It would take a leap of faith.



She hurried over and stepped close to the Doctor, crossing that border from packed dirt and moldy hay to clean tiled floor.



There was a rush of wind, and the surroundings swam violently for two or three seconds.  When the image had resolved again, they stood in the middle section of a long hallway.  It looked like a hospital, sterile, white, clean, but it was empty.  There were no people, and there was no equipment.



``Welcome to Cauldron,'' the Doctor said.



\sectionbreak



``How did you find me?  I just got an email.''



``I'd have to check my notes.  We have ways of finding interested parties.  If I remember right, you were browsing websites, researching ways to acquire tinker-made armor and weapons?''



Jamie nodded.  ``I was.  So many were fakes or scams that I wasn't willing to trust the ones that did look legit.''



``We own several of those sites.  All are fakes.  That might have been where we first noticed your activity.''



``That's a little creepy.''



``Creepiness is an unfortunate reality when you're forced to operate covertly, without a steady customer base.''



``Why?  Why not go public?''



``Countries would go to war over what we have at our disposal.  A way to grant powers to anyone who wants them.  They would want armies of parahuman soldiers.  Even if we did manage to establish ourselves as a neutral party without government interference, Cauldron would be infiltrated by those looking to steal our secrets.  Spies, thieves.''



``And people who wanted to establish a rival business?''



They were reaching the end of the hallway.  The Doctor smiled lightly.  ``And that.  Please, through this door.''



Jamie prided herself on her ability to identify evasions and untruths.  The Doctor was humoring her when she replied to the question about rival businesses.  The idea didn't seem to worry her.  Why?



Jamie stepped through the open door and entered a large room.  As with the hallway, the decor was predominantly white.  There was a desk of white marble with a white leather chair, and two plastic chairs facing the desk.  A modestly sized monitor sat at one corner of the desk, with a compact keyboard placed in front of it, and no mouse.  The space was spartan.



\emph{I'd go crazy in here.  There's no personality to this place}.



Stranger still was the lack of dust.  Since her arrival, Jamie hadn't seen anyone but the Doctor.  How did the Doctor keep everything so clean?



``Have a seat.''



Jamie sat in one of the plastic chairs.



``I like to talk and establish expectations before we begin.  You should know that almost every aspect of this experience can be tailored to your tastes.  Cauldron's \emph{usual routine}, however, is to arrange one face to face meeting.  We'll discuss your budget, your situation and goals, and then we'll peruse a catalog to find something that fits your budget and will hopefully give you the results you desire.  There is a two month waiting period, during which time I will assign you some testing, some regarding your physical condition, other tests for psychological reasons.''



``Psychological?  Is that to make sure I won't flip out and go villain when I get powers?''



``That is not a concern.  Though your question seems to indicate that you hope to be a hero?''  The Doctor made it a half-question, half-statement.



Jamie's brow furrowed.  ``Wait, so you give powers to people who want to be villains?''



``We give powers to \emph{anyone} who pays.  Rest assured, if you wish to end this meeting now because of a pang of conscience, we can see you returned to the barn shortly.''



Jamie hesitated, then shook her head.  ``It's fine.''



``The testing will include blood tests, stress tests, MRI, CAT scan, radiographic scans and a Torsten DNA sequencing.  These scans are primarily for \emph{our} purposes, and if you'd prefer, you can have your family doctor arrange or conduct these tests instead for a small fee.  A larger fee will allow you to skip the tests entirely.''



\emph{Fees and additional expenses}.  No.  The testing wasn't so important that she'd spend her money on it.



``You can conduct the tests however you want,'' Jamie said.



``Good.  You'll need to forgive me, but I must be blunt.  Cauldron operates on a strict policy of secrecy.  It is crass of me to do this, but know that if you pass on any knowledge of what transpired here, we have ways to find out, and we'll be forced to employ countermeasures.  This is in effect even if you decide you do not wish to sign anything.''



``Countermeasures?''



``Our response will reflect the gravity of the offense.  We have clients who have spent hundreds of millions of dollars on the products and services we offer.  It is our obligation to protect them.''



``What kind of countermeasures?  Would you kill me?''



``We try to avoid murder in the course of doing business, not just because of the moral issues, but because it draws attention.  For leaks, our usual procedure is to discredit the individual in question and deploy our in-house division of parahumans to drive them into hiding, remove their powers or both.''



\emph{Try to avoid murder}.  The phrasing implied the Doctor or Cauldron had gone that far before. She didn't like that, and she \emph{especially} didn't like the fact that the Doctor was phrasing things so she'd miss that detail if she wasn't listening carefully.



``It's fine.  I don't intend to break the rules.''



``Few do.  Still, I've done my duty and informed you.  Tell me about yourself, Jamie.  I know your father is in law enforcement.''



``He's a detective, yeah.''



``Does that have anything to do with \emph{why} you're here?''



Jamie frowned and looked away.  ``Yeah.''



``Tell me.''



``A year ago\ldots well, it all started two years ago.  There were two criminals called Ramrod and Fleece.  The local heroes brought them into custody, partially because of my dad's work in tracking the pair down.  Three strikes act applied to Fleece, and Ramrod was in for murder with intent.  They put them in special cells, got them a court date, and everything was normal.  My dad worked to gather the evidence, made some deals with informants to testify anonymously, and everything.  The court process takes a lot longer than it does on TV.''



``Too true.''



``Finally, after about a year of court appearances and one minor appeal they managed to squeeze in there, it was decided.  The pair was supposed to go to the Birdcage.  Except someone broke them out.''



``I think I'm beginning to understand.''



Jamie gnawed on her lip for a second.  Just thinking about it pissed her off.  ``His name is Madcap, and he's a mercenary that specializes in breaking people out of jail.  Sometimes even when they're in the convoy on the way to the Birdcage.  And it's just\ldots wrong.  It's not the way things should work.  Months or years of investigation, good police and good heroes risking their lives to finally catch someone and arrest them, a year of trial, and all it takes is one fucking asshole with powers to free them?''



``And so you've spent the last year trying to find a way to purchase powers, with the intent of righting that wrong?''



``I want to \emph{stop him}.  And not just him.  I want to help things make sense again, even if it means playing unfair because \emph{they're }playing unfair.  Crime should have consequences.''



The Doctor typed something onto the keyboard, paused, and then typed something else. ``Madcap.  Well, the good news is that he isn't one of ours, so there's no conflict of interest. The bad news is that the PRT rated him as a striker seven.''



Jamie's face settled into a grim expression.  ``I know.  My dad has resources.  I took the time to look up Madcap's records.''



``Having looked into your finances-''



``I've got a place in the city that was left to me.  My dad doesn't know about it, so it'd be easy to sell it and not have anyone close to me get curious where they money went.  Current housing market says I could sell it for three-quarters of a million dollars.  I just have to sell it.''



``We can expedite this.  Cauldron is prepared to buy the property from you for seven hundred and thirty thousand dollars, renting it out to you in the meantime if you require it.  We will sell it at our leisure rather than wait for you to find a buyer.''



``I don't need you to rent it to me.  No, that works,'' Jamie said.  She was secretly relieved to have one of the biggest hurdles handled so easily.



``Good.''



``And I have another five thousand that my relatives set aside for my school.  It'd be harder to use that without people getting curious, but it's there.''



``We'll see.  In terms of cost, Cauldron requires that the client pay two-thirds of the total amount in advance, and pay the rest over a six year period or \emph{default}.''



``Meaning you employ those \emph{countermeasures} you talked about.''



``Revoking your powers in the worst case scenario, yes.''



``Is that revoking of powers a part of the process of however you give people the powers, or is it something that one of your in-house capes does?''



The Doctor was typing on the computer.  Without taking her eyes from the screen, she said, ``The latter.  You don't need to worry about someone using a loophole or flaw in the process to take away your abilities.''



The Doctor frowned at the image on the computer screen.



``What?''



The Doctor turned the monitor around.  It showed graphs and charts that made little sense to Jamie.  Clearing her throat, the Doctor leaned forward over the desk and extended one manicured nail to point at a series of labels on a three-dimensional graph.  ``This is the `P' value as related to the cost of the power, with the expected range of powers.  The amount of money you have, even assuming an additional thirty-three percent in payment made at a future date, is probably not going to provide you with the power you'd need to take on a striker-seven.''



Jamie's face fell.  Shaking her head in confusion, she asked, ```P'?  And what do you mean by \emph{probably}?''



The Doctor opened a drawer and retrieved a binder.  She slid it across the desk.



Every page was laminated, labeled with a serial number.  Each page had a picture of a vial with a different colored metallic liquid inside, sitting beside a list of powers.  The bottom half of the page or a second page, depending on the number of powers listed, had a grid with a number assigned to an arrangement of letters.



``No sample provides the exact same powers every time.  The bullet points note examples of the powers gained when the sample was tried on a human subject or a client.  There's typically a common thread or theme connecting powers from a given sample.  One sample might have a tendency to work with the production of acids and a tendency for physical manifestation.  This might allow an individual to turn into a living pool of acid, to secrete acid from his pores or to spit streams of corrosive venom.''



``I don't want a power like that.''



``No.  For one thing, the `R' value of sample J-zero-zero-ninety is very low.  Note the letters on the grid.  The most important ones are the `O', `P' and `R'.  These, on their own, determine roughly ninety-percent of a sample's cost.  O refers to a power's uniqueness.  It's largely subjective, and liable to change through factors entirely out of Cauldron's control, but it is easier to stand out as a hero or villain if nobody else can do what you do.''



``You've already mentioned the other two letters in passing.''



``The `P' value is the raw effect of the granted abilities.  An estimation of the rating the PRT would assign to the powers.  Higher `P', more effective and versatile abilities.''



Jamie nodded.  ``And `R'?''



``Unfortunately, as I've mentioned, there are no guarantees.  A given sample does not provide the same effects every time it is tested.  There are admittedly some dangers involved in the use of our product.  Sometimes there are physical changes that cannot be masked.  You have seen the heroes or villains with glowing eyes or less human features.''



That was sobering.



``The `R' value refers to how predictable a given sample is.  There are some that produce very simple, reliable results.  In sixty-three tests of sample T-six-zero-zero-one, it has only failed to grant a form of flight on two occasions.  Contrast that with sample B-zero-zero-thirty.  It has, in four tests, granted an individual the ability to make things implode, it has created a powerful vacuum in someone's mouth, that draws everything into a portal where it is promptly annihilated.  Sample B-zero-zero-thirty killed the other two test subjects.''



\emph{Killed}.  There was an outside possibility she could die, if she took the wrong one, or if she got especially unlucky.



``How do you test this?  You're talking about a lot of tests, sixty for just one sample, but there's no way people wouldn't notice or that word wouldn't get out if you were doing something like that.''



``As you've seen, Cauldron has resources.''



``That doesn't really answer my question.''



``It does.  Just not as clearly as you want it to.''



Something in the Doctor's tone suggested the woman wasn't going to elaborate further.  Jamie shut her mouth, frowning slightly.



``As you can see here, this graph shows the relationship between cost and the rising `P', `O' and `R' values.''



It was a cube broken into a multitude of smaller cubes, with P as the X axis, O as the Y and R as the Z.  They ranged from white to sky blue to darker blue, purple, red, and finally crimson.  The key at the bottom of the graph suggested that anything beyond dark blue would cost several million dollars.  By the time it hit crimson, it was ranging into the\emph{ hundreds} of millions.



``This\ldots is what you can afford.''  The Doctor hit a key and the graph was reduced to the white and light blue cubes.  ``You could theoretically push into the seven range of `P' values, to put yourself at this Madcap's level in terms of raw power, but you would be forfeiting a great deal in the other two departments.  Your powers would be relatively simple, defaulting to the sort of abilities that countless other heroes already have\ldots and with the low `R' score, you would be risking getting something you do not want.  Physical changes, perhaps, or powers outside of the area you wanted.  Super strength when you desired telekinesis, for a crude example.''



``I\ldots I'm not fixated on anything particular, powerwise.  Flying would be cool, but I'll take anything that works.''



The Doctor tapped a key, and the graph shifted so there were only three rows.  She'd removed the samples with higher uniqueness values.



``Then the question is\ldots'' the Doctor said, ``How much are you willing to gamble?  A hero can beat a superior foe with strategy, tactics and forethought, and I get the impression you're focused enough to put your mind to the task.  Perhaps you'd want to emphasize reliability in a sample over the power it could offer you?''



``Can you zoom in?''



The Doctor did.



``So\ldots how unreliable is a five, if we're talking about `R'?''



``If you decided on a sample with an `R' score of five, I would tell you I could make no promises.  There would be perhaps a three or four percent chance you would experience some unwanted physical changes.  Zero-point-five percent chance that you'd experience changes of a degree that you wouldn't be able to go out in public without drawing notice, even with heavy clothing.  You would, I'd venture, not be buying a particular power, but the broader category of that power.  To use our earlier example, you would not be buying acid spit, specifically, but an \emph{acid power.}''



Jamie looked at the other lines on the graph, ``And I'd be getting something like an `O' of three and a `P' of five.''



``Something in that neighborhood, yes.''



``A power rating of five to Madcap's seven,''  Jamie put her elbows on the edge of the desk and her head in her hands.



``There's a chance you could get lucky and achieve a power with a greater `P' value than expected.''



Again, that misdirection.  Jamie shook her head.  ``And a roughly equal chance that I could get unlucky, since it's an average.''



``Admittedly true.''



``Is there anything else I could do?  A way to get better results?''



``We have options, but I don't know that they apply to your case.  I mentioned the psychological testing earlier.  You should know that an individual's personality, mental state and background do seem to have a great deal of effect on the resulting power. I would even say it's one of the primary factors, outside of the sample itself.''



Jamie wondered momentarily how her own mental state would influence her powers.



The Doctor went on, ``We have a package we call `Shaping', and another we call `Morpheus'.  Both are intended to make the most of the two month waiting period and help a client reach an ideal mental and emotional state.  It's often purchased by our high-end customers, to refine the powers they want and help ensure there are no untoward effects. For a low-end customer such as yourself, I don't know that it would suit your needs.  You would be buying a lower quality sample to pay for the package\ldots perhaps if you were someone who wanted powers for recreational purposes.  If you wanted to help guarantee that you got the ability to fly, for example.''



Jamie nodded.



``There's the Nemesis program, but you already have an opponent in mind, and I expect you're more interested in a fair fight than having an opponent you're guaranteed to succeed against when it counts.''



``Yeah.''  This Nemesis program\ldots how many prominent heroes or villains were out there that had faked or staged confrontations like that?



``Hmm.  Nothing else springs to mind as our packages go.  When we design an additional feature or program, we tend to aim it at our more wealthy customers.''



``You guys are doing lots of testing.  Could I do something like help with that?  Or something outside of these packages and programs?''



``Perhaps.''



``I'm serious, I'm hard-working, and I stick to my guns.''



``It's our tendency to require that any client be prepared to perform one unspecified favor for us at a later date.  Usually a simple task or a week of service.  It serves as a way to cover our bases without revealing too much in respect to our operations.''



``Very \emph{Godfather}.  Do these favors mean doing anything illegal?''



``Sometimes.  But no, often it is a request to meet someone, to pass on a message, or help manage an information leak, a show of force to scare someone who is poking too deep.''



Jamie's leg bounced nervously as she looked at the screen.  ``And?''



``If you agree to perform \emph{three} favors at a future date, and I suspect we could extend something of a discount.''



The Doctor hit several keys, and the graph extended a little in every direction.  Where it had been white and light blue, it now showed cubes of dark blue.



``What would you ask me to do?''



``I don't know yet.  I prefer to leave that option open.''



Everything in Jamie's gut told her there was some small lie or misdirection in there.  Either the Doctor did know what she wanted to ask for, or she knew her customer wouldn't like what she heard.



Whatever these favors were, all she could do was hope she could do enough good to counterbalance any wrongs she'd have to commit.



``Alright,'' Jamie said.  ``Sounds like a deal.''



\sectionbreak



Jamie's fourth visit to Cauldron was less out of her way than her first.  She entered the same way as before, but this time the hallway from Cauldron's location was transplanted into the middle of her apartment.  She wasted no time in stepping through.



The Doctor was not waiting for her, but she knew where she was going.  She strode down the empty, spotless hallways, past innumerable matching doors.  There were no windows in this place.  Nothing peeking into the outside.



Still, she knew where she was.  She'd checked the GPS data on her necklace.  The Ivory Coast.  The west coast of Africa.  It was dangerous information to have.



\emph{If I tried to open one of those doors, would it be locked?  What would be inside?  Or would alarms go off, my chance here spoiled?}



She'd been here twice since her first meeting.  Both times, she'd had her psychological testing.  She'd also had a full workup done.  The psychiatrist had been a young-looking white man, the doctor a heavyset Greek.  They'd said little beyond what they needed to for the testing, and had volunteered nothing about Cauldron.



She made her way to the room where she'd done her stress test.  Here, she'd run back and forth with steadily increasing speeds until she couldn't run anymore.  She'd rested, then run again, then again, until she couldn't even stand.



The Doctor was waiting for her.  A metal canister sat on a table, and there was a sturdily built, cushioned chair sitting close by.



``You're ready?'' the Doctor asked.



Jamie nodded.



``If you'll change into this, we can preserve your clothes for the return trip home.''



Jamie took the offered clothing, a plain gray bodysuit that would cover everything from the neck down.  A word in blocky black letters on the front read `Jamie' while one on the back read `Client'.



There was no indicated change room, and the Doctor was focused on the canister and the stack of papers she was setting down on the table.  Jamie changed where she stood, folding her clothes and setting them on the edge of the table.



``Sit.''



Jamie sat in the chair.  Comfortable.



``Sample T-one-one-seven-seven, with the agreed upon addition of Sample C-zero-zero-seventy-two.  This is correct?''



``Yes.  It's what I paid for.''



``Read and sign here.  And there are stipulations on, let me see\ldots pages twenty-six and twenty-nine that you need to sign as well.''



Jamie leaned forward and read through the contract.  It was every term they'd agreed upon, legalese and politely worded warnings about the hell Cauldron would try to bring down on her head if she broke the terms of the contract.  There were pages of receipts covering the financial transactions, and pages more of details about her own medical and psychological evaluations.



There were two stipulations to agree to.  One for the three favors she'd agreed to perform.  Another on the psychological testing.



Nine years ago, she had been kidnapped for use as leverage against her father.  She had been held in their custody for three days.  No food, six water bottles to drink and no bathroom.  She'd gone to the washroom in the corner, had removed one sock to keep the pee from making its way across the sloped hardwood floor.



She'd assured the psychiatrist that she had gotten over any of the trauma and any fear of the dark that had stemmed from that incident.  It was her father that'd had a hard time dealing with the event.



She'd been young then, and the event hadn't really stuck in her memory.  But she couldn't shake the idea that the kidnapping might have left some lingering effect on her that would taint the process.



``You haven't eaten?''



``Nothing since this time yesterday.''



``You don't have any colds, no aches and pains?''



``No.''



``That's too bad.  The sample we use to moderate and control the effects of the finished products has a short-lived regenerative effect.  This is one of the selling points we offer to the clients we find in hospitals and the like.  Some have even recovered or partially recovered from life-long disabilities.  We've had reports from people who were mildly ill when they gained their powers, who found they never got sick again.  It would be nice to verify this.''



``You couldn't have told me that before?''



``It could easily be a placebo effect.  Not worth a rescheduling.  You're comfortable?''



``Sure.''



The Doctor unscrewed the canister and withdrew a vial.  It was no longer than a pen and no thicker than one of the Doctor's fingers.  ``The faster you drink it all, the quicker and cleaner the transition is.''



``You said something about a dream quest?''



``Some experience it.  Some don't.  Don't be concerned if you don't.  Simply relax to the best of your ability and stay focused.  The higher and more pronounced the physical reactions like your heart rate, sweating, adrenals, and emotional response, the greater the chance of a physiological change.  I recommend that you keep from dwelling on any stressful thoughts or memories.  Just stay calm and try to relax as much as you're able.''



``Isn't that like asking someone to not think of a blue elephant?  They're going to think about a blue elephant.''



``I stress, only a small percentage of people experience enough stress that they undergo any physical change.''  The Doctor removed the stopper from the top of the vial and carefully handed it over, not letting go until she was sure Jamie had a firm grip.



Jamie held the vial for several long moments.  ``Now?''



``When you're ready.''



Jamie tossed it back like she'd seen people throw back shots of hard liquor.  She coughed as it coated the inside of her throat, her saliva doing little to nothing to help it down.  The Doctor reached out, and Jamie handed her the vial.



It began to burn, the intensity increasing second by second, until she was convinced it couldn't get any worse.  It did.



``Hurts,'' she groaned, trying to push herself to a standing position.



``It'll get more severe before it gets better.  Stay in the chair.''



``Didn't tell me,'' she could barely speak with the way her chest felt like it was caving in on itself.



``I didn't want to alarm you before we began.  It's normal, and it \emph{does} get better.  A minute, maybe two, and you'll be surprised at how fast the pain goes away.''



She clutched the arms of the chair.  As unfathomably bad as it had been just moments ago, it kept getting worse.  She had to endure another \emph{two minutes} of this?  It felt like the burning inside of her was melting through the walls of her throat and stomach.  She could imagine the tissue blistering and dissolving, expanding outward until it touched on her lungs and her heart.



As it seemed to consume her lungs, her breathing began to dissolve into breaths too quick and small to bring enough oxygen into her lungs.  Darkness began to creep in at the edges of her vision.



``Relax.''  The Doctor's voice sounded far away.



She was panicking, and the \emph{idea} that she was panicking made it worse, because it could mean she'd \emph{change}.  She might look different.  Scales, spines, metallic skin or something else.



The darkness swallowed her field of vision and she felt as though it were creeping over her skin.



What had she been thinking, doing this?



\emph{Have to calm down}.



She'd taken up Tai Chi when she was thirteen, something one of her therapists had encouraged to deal with stress.  She couldn't move here, and it was impossible to stand, let alone do her exercises, but she could try to reach that mental state.  She attempted to take deep breaths, but she couldn't even tell if she had air in her lungs or if she was breathing in or out.  She tensed the muscles in her fingers and toes, then forced herself to relax them.  She did the same with the muscles of her hands and feet.  She worked her way up through the entirety of her body, focusing on that simple action of tension, relaxation.



The pain didn't stop, but she felt disconnected from it, now.  She was calmer, focused.  She felt as though she were adrift in a vast, empty space, aware of every part of her body, the wholeness of it, and nothing else.



An incoherent image flickered across her mind.  A landscape of twisted biological shapes that seemed to alter with every passing second, changing into something completely different.  An archway of bony growths disconnected and became a bridge over a crevasse.  Then a hill.  Yet it all seemed to change with \emph{logic}.  It was just a logic she couldn't comprehend.



The ground split.  Chasms tore into the surface, dividing it, and-



Another image.  Earth.  It was as though she was looking at everyone's face and every object and every living thing on the planet at once, from every angle, but then she was looking at a \emph{different }everyone and everything, then another.  It dawned on her that it wasn't \emph{her} doing the looking.  She was a bystander.  Before she could realize what this \emph{other} was looking for, the scene changed again.



Utter blackness and silence.  It was only in this stillness and quiet that Jamie realized there was an undercurrent.  An \emph{impression}.  She hesitated to call it an emotion.



Reaching.  It was the only word she could use to place it, and it didn't quite fit.  It was an action that was simultaneously frustrated and frustrating.



The pain cleared away so quickly she thought she might have imagined it.



She was on the ground, she realized.  On her hands and knees.  Tears ran down her cheeks.  Not all were from the pain.  Some were sympathetic.



``What was that?  What did I just see?  It wasn't a dream.  It wasn't what you described.''



``Roughly half of my customers ask questions similar to yours after they've transitioned.  I always say the same thing.  \emph{I don't know}.''



Even in the daze she was in, Jamie's instincts told her the Doctor was lying.



``I expect you'll retain the memory better if you don't try too hard to hold onto it.''



The strange things she had seen didn't seem to matter anymore.  ``Did I\ldots change?  Is my body different?''



``You glowed briefly, but that passed.  You look the same as you did.''



Jamie nodded, too worn out to feel relieved.



``I'm going to leave, now, for my own safety.  I recommend sitting and resting before anything else.  When you're prepared, stand and see what you can do to exercise your new abilities.''



The doctor was halfway to the door when Jamie shifted her position and prepared to climb into the chair.  Relief was surging through her.  She hadn't become a monster.  She hadn't lost her mind.  This was for real.  What she had seen, it was too profound to mean anything else.  Even a hit of LSD wouldn't have given her visions as clear as that.  Not that she'd done LSD.



Though she didn't feel dizzy, she found she lacked the sense of balance to stand, and tipped forward.  Between one heartbeat and the next, everything seemed to \emph{click}.  She felt as though she were floating in slow motion rather than falling, her body \emph{thrumming}.  She extended one arm toward the arm of the chair to catch herself, but she underestimated the speed and strength of the movement in the midst of this slow motion world.  The chair was sent flying, skidding across the floor.  She fell hard, the moment over, her fall no longer slow motion.



On the other side of the room, the chair hit the wall and shattered.



``Seems you have something.  Congratulations,'' the Doctor said.



\sectionbreak



Madcap hit one of the armored PRT vans hard enough to make it roll.  The driver of the second tried to steer clear, but Madcap stepped into the path of the incoming vehicle.  It struck him and the vehicle virtually bounced off of him, the hood crumpling as though it had hit a telephone pole.



He rolled his shoulders, and then kicked the vehicle.  It skidded along the road and collided with the third truck, which had already pulled to a stop.



Which left only the task of freeing his clients.



``Stop!''



Madcap turned.  Jamie stood in the middle of the street, opposing him.  Her low-budget costume consisted of a black bodysuit and a domino mask.



``You're cute.  Nice body, and the costume is a nice mix of pathetic and adorable in a three-legged-puppy kind of way.   But you don't want to try to stop me.  I hit pretty damn hard.''



The mention of her costume embarrassed her.  She hadn't had the money after buying her powers.  \emph{Still,}\emph{three legged puppy?}



Madcap, by contrast, was wearing a customized costume that had cost no small amount of money.  A faceguard covered the lower half of his face, and was imprinted with the image of a wide grin.  Black facepaint surrounded his dark eyes, accentuating the whites, and a pointed black leather cap connected to the mask and his costume.  His armor was more aesthetic than functional, and featured broad, spike-studded pads.



``I hit pretty hard myself,'' Jamie replied.  A glance over her shoulder revealed that the two men who'd been driving the containment van nearest her were running.  She knew it was empty, a decoy.



She wrested the bumper free with a tug and then swung it at Madcap like an oversized bat.



He blocked it with one hand, and the scrap of metal slipped from her hand and went sailing into the nearby cornfield.



Then he slid forward and tapped the flat of one hand against her chest.  She bounced off of the ground and fell in a heap.  It took her one attempt at standing before she realized it was futile.



Two PRT soldiers stepped forward to try to spray him with foam, but he dispatched both with a throw of something that looked like a thick frisbee.  With nobody left to stop him, Madcap proceeded to tear doors off the containment vans until he found the prisoners.



Jamie tried to move again.  Everything hurt too much.



``No,'' Madcap said.  ``Leave her be.''



She opened her eyes to see two villains, a male and a female standing nearby, with Madcap standing between her and them..



``She looks like a right morsel,'' the man commented.



``Not saying she doesn't,'' Madcap said, ``But hands off.  You paid me to free you, and I can't do that if you're fucking around.''



``Spoilsport,'' the woman said, teasing.  ``Come on.''



Then they were gone, and Jamie let her head rest on the pavement.



\sectionbreak



``My power didn't work.  I was strong, and then I wasn't.''



``There are going to be nuances,'' the Doctor said.  ``We \emph{could} help you investigate the intricacies of your ability.  But that would cost you.''



``Everything costs something, here.''



``I have another idea in mind.''



``Another idea?''



``Consider this your first favor to us.  Cauldron would be much obliged if you could join the ranks of the Wards, and then graduate to the Protectorate as soon as possible.''



``The Protectorate?  Why?  To sabotage it from within?  Steal information?  I don't want to do anything like that.''



``Just join.  That's all I ask.  If nothing else, it would mean you had resources and training to develop your powers and achieve your own goals.''



Jamie frowned, looking at her gloved hand.  She had been contemplating joining anyways.  It meant one favor out of the way, relatively harmless, which was good, but there was little doubt that Cauldron wanted her in place for a reason.



\sectionbreak



``Round eight, puppy?''  Madcap said, ``Maybe you can finally win one!''



Jamie charged him, and the rest of her team followed soon after.



Madcap leapt to one side as Legend fired a series of beams at him.  The villain plunged into and through the concrete wall of the jail, and Jamie was only steps behind him.  She saw him rounding a corner and gave chase.



He wasn't in the hallway.  There wasn't even debris from where he'd torn his way through yet another wall.



She activated her power.  Time seemed to slow down as she sped up.  She snapped her head to look \emph{up} and saw him in the middle of a leap over her head.  He'd timed it perfectly, so he would be above her when she rounded the corner.



Except she was faster, and she could hit harder than he could.  Given a chance.



Her elbow caught him while he was still airborne, and unable to dodge.  She slammed him into a wall, and followed up with a leaping kick while the effects of her power still coursed through her.



Madcap rebounded off of the wall as though he were made of rubber and ducked beneath her incoming kick.  Twisting around as he rose back to a standing position, he got a grip on her from behind in the same moment her foot hit the wall.  Heaving, he hurled her down the length of the hallway.



\emph{Calm}.  She had to be calm, concentrate.  Even as she flew through the air, she let her power build up inside her, then released it.  With the half second of effect it gave her, she contorted herself to touch the wall with one foot, then lightly kicked it to turn herself toward the ground.  She landed in a crouch, sliding from the inertia, and began charging up for another go.



Legend's lasers tore into the spot where Madcap had been a half second ago.  The villain sprinted toward Jamie, moving faster with each step.



``Battery!'' Legend called out, ``Stop him!''



She held on, concentrating.  She let a deep breath pass through her lips.



Sticking one foot out in front of him, Madcap changed directions, heading straight through the wall.  Plaster exploded around him.



She released her power, and for just seconds, she was strong, she was almost invincible, and above all else, she was \emph{fast}.  She ran forward, plunging through two walls in her pursuit.  Emerging from the second wall, she came within a few feet of Madcap.



He turned on the spot, reaching out to block her strike or grab her.



But she didn't give him the opportunity to do either.  Instead, she spent the rest of her accumulated power in a single burst, pulling at the metal of a nearby chair.  It fell over, sliding into Madcap's path.  The metal legs caught on his own legs, one sliding just beneath his descending foot.  He stumbled.  He exerted his power, causing the chair to crumple and explode before he stumbled any further and fell.\emph{  }



She heard a brief chuckle from the man as he turned to make his escape.



Legend had taken advantage of that momentary delay to get in position.  He caught the villain with a laser blast.  Madcap tumbled, got his feet under him and darted for cover.  A laser blast turned the corner to follow and smash the villain into the ground.  Legend shot him again while he was down, and the man was unconscious.



``Good job, Battery.'' Legend spoke with a smile.  ``Finally, huh?''



``Finally,'' she said.



\sectionbreak



``I really don't want to go to the Birdcage,'' Madcap said.  He was covered in containment foam from shoulder to toe.



``You've committed somewhere in the neighborhood of a hundred felonies,'' Legend answered him.  ``I don't think you have many options.''



``Felonies, sure, but I haven't killed anyone, and that's got to be worth something.  Now, this is just a suggestion, but what if I switched sides?''



``Get real,'' Battery replied.



``I'm serious, puppy.  You guys need more bodies on the field, I don't want to go to the Birdcage, it's win-win.  I'm strong.''



``You've spent nearly six years perverting the course of justice for others,'' she replied.



``And now I can make amends!'' They had removed his mask, but his real smile was almost \emph{more} mocking than the one that had been styled into the mask.



``You spent the last five and a half years getting people out of the Birdcage, claiming to be against it and everything it stood for, but now you're willing to work to put people in there?''



``Maybe you've changed me.  Your good looks, your winning personality, and your diehard persistence in the face of \emph{so many defeats} at my hand.''



Battery looked at Legend, ``Don't suppose we can gag him?''



``Sadly, no.  And he raises an interesting idea.''



``He's going to run the second he gets a chance.''



``There are options.  Tracking devices, or perhaps Myrddin can put some countermeasure in place.''



``I'm down for any of that stuff,'' Madcap said, casting a sidelong glance at Battery.  He grinned, ``But I want some concessions.''



``Concessions?  You asshole.  You should be glad that we're even \emph{entertaining }this asinine idea.''



``I think you'll find them pretty reasonable,'' Madcap said, more to Legend than Battery.



``Let's hear it.''



``I think this would work best if I took on a new identity.  New costume.  My powers are versatile enough that I doubt anyone's going to draw a connection.  It also means I don't have any enemies or any paranoid customers from my shady past coming after me.''



``That could be arranged.''



``And I want to be on \emph{her} team,'' Madcap said, pointing at Battery.  He smiled.  ``Puppy changes to a new city, I go with.''



``Hell no,'' Battery said.



``\emph{Why}?'' Legend asked.



``It's funny,'' Madcap said.  ``It's going to irritate the piss out of her, and I've got just a little bit of a sadistic streak in me.  If I don't channel it \emph{somehow}, this just isn't going to work out.  Just give me this, and I'll be a boy scout.''



``Boy scout?  You'll be on your best behavior?''  Legend asked.  ``This would be more than even regular probation.''



``\emph{No.}'' Battery said.



``\emph{Yes}.''  Madcap answered the man.



``\emph{No},'' Battery said, stabbing a finger at Legend.  ``I've been a \emph{damn} good hero for you guys.  My record is spotless, I've put in the hours, I've put in the \emph{overtime} hours.  I've done the jobs nobody else wants to do, the unpaid volunteer crap, the patrols at the dead of night when nothing happens.  \emph{This} is a punishment.''



``You're right,'' Legend sighed, ``It would be a heavy burden for a good heroine.  So it's up to you.  You decide if Madcap joins the Protectorate or not.  I won't judge you if you say no.''



``But you think I should say yes.''



``I do, if it makes us stronger in the long run.''



Battery looked down at Madcap, and the villain offered her an exaggerated pout, his eyes large, his lower lip sticking out.



``Fuck me,'' she said.  ``You're going on paper as the one making the call, Legend, and you're taking the hit if this backfires.''



``That's fair.''



``Yes!'' Madcap grinned.



``I've died and gone to hell,'' Battery muttered.  It was everything she'd become a hero to prevent.  A villain evading his rightful justice.  But she knew it was for the greater good.  They \emph{did} need more heroes out there.



``I already have a name in mind for my goodie-two-shoes costumed self,'' Madcap grinned.  ``You're going to like this one, puppy.''



``You're going to have to stop calling me that,'' Battery warned him, ``Or your identity as Madcap is going to become public knowledge, \emph{fast}.''



Madcap rubbed his chin.  ``Maybe.  I'll agree to stop if you accept my name.''



She sighed.  ``I already know I'm going to hate this.''



``You'll \emph{love} it.  \emph{Assault}.  Get it?''



It took her a second to process.  ``No!''



``No?  But it's perfect.  We'll be a pair!  People will know from the second they hear it.''



``The connotations are horrible!  No!  You're not allowed to change the intent of my name like that!''



``Fine, fine.  Point taken.  \emph{Puppy}.''



Battery looked at Legend, ``Can I maybe get a raise, for putting up with this?''



The leader of the Protectorate folded his arms.  ``Something can be arranged.''



\sectionbreak



``It can be a coffee,'' Assault told her.  ``Or a beer after a night of patrols.  Nothing fancy, low stress.''



``\emph{Low} stress?  You're forgetting the part where I'd be spending more time in your company than I have to.''



``Hon, you need to \emph{unwind}.  Relax.  You're too rigid, and I know for a fact that you haven't had a boyfriend \emph{or a girlfriend} in the two years I've worked with you.''



``Stop implying I'm into women, Ass.''



``Well, you know, you keep turning me down, so it kind of makes a man wonder.''



``I've been too busy, and even if I \emph{did} want to date, rest assured, you would be my last pick for company.''



``So hurtful!''  He pressed one hand to his chest.  ``Look at me, I'm like a knight in shining armor, now.''



``A wolf in sheep's clothing, more like.''



``Arooo.''



Miss Militia stopped in the doorway.  ``Need rescuing?''



``If you could put a bullet between his eyes, I'd owe you one.''



``No can do.''  Miss Militia offered her an apologetic grimace.  ``You okay, though?''



``I'm okay, thanks.''



Miss Militia headed on her way, and Assault smiled, ``Listening to her, you'd think every second in my company was torture.''



``Oh, you'd be surprised,'' Battery retorted.  She turned and topped off her cup of coffee, finishing the pot.  Assault stepped in and began preparing the next pot.  It would have been a nice gesture if it weren't for the smug look on his face.



``Come on.  Give me a chance.  Let me know what it takes to get one night of your company.  Tell me to bring you a star in the palm of my hand, or slay a dreaded Endbringer, and I'll get it done.''



``You'd just find some loophole and bring me a plastic star or kill an Endbringer in a video game, which would only give you an excuse to harass me further.''



``Then think of something else.  Anything.''



Battery sipped on her coffee.  ``Anything?  Armsmaster was looking for volunteers for some unpaid work at one of the primary schools.  I already said I'd do it.''



``You do all of that crap,'' Assault rolled his eyes.  ``It'd be admirable if you weren't trying so ridiculously hard at it.  It's like you're trying to make up for some wrong you think you've committed.''



Battery frowned a little.



The grin dropped from Assault's face.  ``Hey, seriously?''



She shook her head.  ``No.  No wrong committed, real or imagined.''



``But the way you looked just now-''



She interrupted him.  ``If you come on this errand with me and do part of the speech for the kids, I'll \emph{maybe} consider \emph{possibly} going out with you for lunch \emph{someday}.''



``Excellent!''  Assault grinned.



He strode off, looking like he'd just won the lottery.



She smiled.  If he only knew this was her shot at some clean, innocent payback.  The squealing, screaming grade schoolers, all fighting and pulling on your costume and demanding demonstrations of powers and constantly asking questions.



And he'd have to put up with it.



She would relish this.



\sectionbreak



``\ldots{}And caught out little suck-a-thumb.
Snip!  Snap!  Snip!  The scissors go;
And Conrad cries out  Oh! Oh! Oh!\ldots''



Assault read from the book of poems, and every one of the ninety kids that sat around him were leaning forward, eyes wide.



``He's so good with kids,'' the librarian murmured.



``Of course he is,'' Battery said.  Maybe there was a hint of bitterness in her voice, because the librarian gave her a funny look.



She plastered a fake smile on her face to assuage the woman's doubts.



``\ldots{}both his thumbs are off at last!''  Assault finished.



The kids squealed in delighted horror.



\emph{Pain in the ass, }she thought.  \emph{If I were reading that one they'd all be crying}.



Battery's phone vibrated.  She excused herself from the librarian's company and checked the display.



Customer wants product hand delivered by known parahuman.  Package waiting in your apartment.  Second task.  -c



Cauldron had sent it to the phone the Protectorate gave her?  To a number that only the Protectorate had?  Did that mean something?



She deleted the message.  It would be easy enough to handle.  If the recipient wound up being a villain at a future date, she'd stop them, put them away.  This would just be a delivery.



Assault caught her eye and a slow smile spread across his face, as the little girl in his lap read some of the next poem.  The look was smug, sly.  He knew exactly how much this was irritating her.



``Jackass,'' she muttered.



But she couldn't stop a smile of her own from spreading across her face.



\sectionbreak



The glass in the little window of her front door was shattered.  It fell on her feet as she pushed the door open.



``Ethan!''  Battery called out.



``You're okay,'' Ethan said, as he came down the stairs.  He was still in costume.  Only a single cut marked his cheek.



``I didn't know where to find you, and since the cell phones don't work anymore, and you weren't at headquarters, I thought I'd come here.''



``I know.  I thought much the same thing, but I came here first.''



``You're okay?''



``I'm okay, puppy.''



She punched him lightly in the arm.  She didn't resist as he swept her up in a painfully tight hug.



``We should go on patrol,'' he said.  ``This is going to be \emph{bad}.  They're kicking us while we're down.''



``Right.  Patrol together or apart?''



``Together at first, assess the situation.''



``Okay.''



``A courier dropped this off for you,'' he pointed at a small envelope on the hall table.



She saw the undercase `c' on the front and felt her heart sink.



``Puppy?''



She picked up the envelope and checked the contents.  A slip of paper, blank on both sides.



A joke?  A reminder?  The last one had been two years ago.



``Let's go,'' she said, crumpling it in her fist.  She charged up and ran, and Assault crossed a similar amount of distance with his long and powerful leaps.



She covered more distance with the start-stop motion of charging and running than she did just running, but it made for a halting progress where Assault simply continued forward.  He made some headway on her.  She knew he'd stop at some vantage point to wait for her.



As she stopped to charge, she felt a tingle from her hand.



The note?



She spent the energy of a charge, but she didn't run.  Again, that tingle.  She used her ability to manipulate electromagnetic energy and focused it on the note as she smoothed it out.



A pattern emerged: simple black lettering.  A second after they'd appeared, the paper started to smoke.



She had only a few seconds to read and process the message before the paper ignited.



Siberian and Shatterbird are to escape the city, and our business with you will be done. Thank you.   c.



The burning scraps drifted to the road around her, but she only felt cold.



Every action had its consequence.





