





``\ldotsMan, oh man, did you ever fuck the dog, here.''



\emph{Blaming me}?



I'd failed.  I'd taken on the world ending threat and come up short.  Why had I even expected to be able to do anything?  Arrogant.



But someone else responded to the accusation.  ``We did no such thing, Tattletale.  Working with the knowledge we had, we put our best foot forward, as did the others.  The fault does \emph{not} lie with us.''



It was the Doctor, uncharacteristically irritated.



Well, Tattletale was good at getting a rise out of people.



``Do I need to repeat myself, Doctor?  You wanted to take charge, you proposed this scenario?  Great.  Except you \emph{didn't} put your best foot forward.  It fell apart as a result, and now we're in a worse place than ever.  The dog is \emph{fucked}.  Thoroughly.  All available holes.''



``You don't need to repeat yourself,'' the Doctor said.  ``Please.  Your meaning is clear.''



``Can you stop talking about fucking the dogs, now?'' another young woman said.  Rachel, I suspected.



``Let's be honest, Doctor.  This was a critical moment, maybe the most critical, and you held back your best cards.  You could have evacuated most of the people there, and you didn't.''



``If we had tried and failed, we might have lost the ability to easily move people between worlds.  Do us both a favor, Tattletale, and stop pretending you're a brilliant individual.  You have access to a lot of information, but that doesn't equate intelligence.  An \emph{intelligent} individual would recognize that they don't have all of the facts.''



\emph{Oh hell}.



I sat up, ready to intervene, and I felt something \emph{off}.  Enough that I gave up on stepping between them.  I opened my eyes, but nobody was in my line of sight.  My hand and lower body were intact.



``We're sinking down to base insults?  Trust me, I'm \emph{way} better than you at that, Dr. Mengele.  I get that you're upset over losing Eidolon, but let's \emph{not} cross a line and become enemies.  We can't afford to add more conflict to the pile.''



\emph{Losing Eidolon}?



Oh hell.



``I was merely stating the facts: namely that \emph{you} don't have all of the facts.''  The Doctor sighed audibly.  ``I'd \emph{hoped} you had something of import to share when you called me in.''



My body was intact, but it didn't feel right.  I experimented, tapping the thumb of my `new' hand against the individual fingertips, then repeated the process, mimicking the movements with my other hand.



``You've already shown you have \emph{one} group of soldiers you've been holding in reserve.  I know you've got more.  Weapons, soldiers, tools, tricks.  You asked some of the best and brightest of humanity to go fight, as phase A in a series of plans you have in mind.  You barely \emph{care}.  So you move on to plan B.  \emph{That} didn't fucking work.  So are you going to throw away more lives, to \emph{maybe} stop Scion, now?  On to plan C?''



I clenched my hands, then stretched my entire body.  The sensations matched but it still felt out of sync in a way I couldn't place.



The Doctor responded, her tone overly patient, ``If we'd gone all out, an upset of some sort might have spoiled all plans at once. Then where would we stand?''



``If we'd gone all out from the outset, we might have stopped him.''



``Then answer this, Tattletale, are you telling me you didn't have any idea about our plan B, plan C and all of the other contingencies, or are you telling me you knew, but you said nothing?''



There was a pause, Tattletale declining to respond.



I glanced around the room.  It was dark, and there were curtains at the far end, drawn shut.  There were four beds, but two of the four were empty.



A girl with banana yellow hair and feathers sticking out of her scalp sat on the bed that was to my left and across from me.  She was sitting on the bed, over top of the covers, with only a folded blanket bunched around her feet.  She wore a sky blue shirt, bright orange shorts and lime green eye shadow. Her body language wasn't a hundredth as vibrant as her clothing.



She glanced at me, and I looked away, not wanting to look like I was staring.



I opened my mouth to speak to the yellow-haired girl, but Tattletale started speaking, and I shut my mouth to listen.  I could tell she was in the next room, by the volume and direction of her voice.  ``\ldotsI had an idea, but I'd expected you to play your cards if worst came to worst.''



``A good lawyer won't ask a question on the stand if they don't already know the answer they're going to receive.  You should take that under advisement.  With the information you have available, you shouldn't ever make assumptions.  The only person you can blame when you're proven wrong is yourself.''



``I feel\emph{ pretty} confident I can blame you on this one, Doctor.''



``Do what you need to in order to make peace with yourself.  At this juncture, it might be all you can do.  Buying time and making peace with things at the end.  Thank you for wasting my time.  \emph{Door}.''



Tattletale didn't respond.  I could only assume Doctor Mother had left.  I reached out for my swarm, and I found for the first time in months that there weren't many nearby.  How long had it been since I slept and didn't have an emergency swarm nearby for self-defense and investigation?  Since I didn't leave hundreds of thousands of spiders spinning threads of silk?



That wasn't to say there weren't \emph{any}.  There were bugs throughout the building, but they hadn't moved until I woke up.  Spiders in corners, bugs in the walls.  A hospital, newly built judging by the freshness of the wood.  I could smell it.



There were tents just outside, set on grass that was just starting to die.



I hadn't even registered it consciously when I visited New Brockton Bay, but the grass had been fresh, alive.



It had been \emph{days}.



I swung my legs over the edge of the bed, sliding them out from under the sheets.  I realized I was wearing only the hospital gown.



My costume-



-Would be destroyed, I realized, belatedly.  The lower half, anyways.  No reason to expect the silk would last if the flesh and bone had been obliterated.



Which raised \emph{really} strange thoughts on the particulars of having my legs rebuilt.  I'd spent years running as a matter of routine.  A part of me had been \emph{proud} of the way I'd honed my body, built up my stamina.



Had they rebuilt my legs with that same strength and stamina?  With the muscles reflecting the regular exercise?  If they had, was it really \emph{my} strength?  If they hadn't, could I deal with it?  Work my way back to where I had been?



If humanity even survived that long.



I needed to go to the bathroom, which made me think of other things.  Had my private parts been reconstituted?  Had Panacea paid any particular attention to the redesign or accuracy of the architecture or plumbing?



Or had it been \emph{Bonesaw} that fixed me up?



My skin crawled at the thought, heebie-jeebies from head to toe.  No bugs involved.  The sensation only served to remind me of how alien the new body parts felt, reinforcing the creeped out feeling.



\emph{Someone found a powerful regeneration-granter and healed me.  Bonesaw and Panacea had nothing to do with it}, I told myself.  \emph{Nothing to do with it}.



The first bugs in the hospital were starting to make their way to me.  They crawled up the sides of the bed and up onto the hospital gown I wore.  I eased my feet down to the cold tile and steadied myself against the bed.



My body was okay, but I felt out of it in the same way I might have if I'd slept in too long.



Not that I'd had that luxury in some time.



Maybe it was odd, to think about things in this sense, to be concerned about my swarm or my body or the fact that I was tired.  Part of that might have been an unconscious form of procrastination.



``Hey,'' the yellow-haired girl spoke.  She was quiet, but the utterance carried across the room.



I'd been staring down at the foot of the bed.  I looked up at her.



``You okay?  If there's pain, or if you don't feel okay to move, I can hit the button to call someone.''



Her voice was attention grabbing, the pitch and tone shifting very deliberately.  Done badly, it might have sounded like she was over-enunciating.  She leveraged it well enough that it didn't sound that way, nor did it detract from the sympathy she was expressing.



I was a little caught off guard by it.  Left wordless, I shook my head.



``Things are bad, but I guess you heard that much,'' she said.



``Yeah,'' I managed.



``I'd explain, but your friends would probably be kinder.''



I shook my head a little.  ``You don't know my friends.''



``They cared enough to sit by you.  One or two of them even held your hand during the tougher moments.''



``Tougher?''



``Panacea said your nerve endings were being reformed, and it was pretty raw.  So you had a lot of fits, like seizures.''



``Oh,'' I said.  ``It's been a few days, I'm guessing?''



``I guess.  I moved in here last night, and you were still out.''



I felt my heart sink.  It was confirmation.  Scion was still active, and had been for at least one day.



``How bad is the situation?'' I asked.



She glanced at the door.  ``Bad.''



``That's not telling me anything.''



``\emph{Really} bad?''



``Casualty numbers?  Key deaths?''



She shook her head.  ``I don't- I never followed any of the cape stuff.''



``You're a rogue, then,'' I said.  \emph{And an ex-member of the Birdcage, if I remember}\emph{right.}



``Yeah.  Canary.  I was a singer, until midway through twenty-ten.  Indie, but I was breaking through to mainstream, some radio stuff.''



I nodded, not really caring.  I wanted more details, and I didn't.



``Another Earth, another time, another society,'' she said, more to herself than to me.



I moved and flexed my legs, trying to judge if the old musculature was intact.  It felt more out of sync than my hands did.  It wasn't that I wasn't ungrateful, but\ldots



No, not worth moaning over it, one way or the other.  I had my life, I had an intact body.



``Do you know if this is even remotely salvageable?'' I asked.  ``Humanity?  Civilization?''



She shook her head.  ``No.''



Was that a no, it wasn't salvageable, or no, she didn't know?



I wasn't sure I wanted to ask.  I saw Aisha poke her head in, glancing into the room.  She met my eyes, then disappeared.



``Well,'' she said, ``They're still fighting.  Kind of.  So there has to be something to fight for, right?''



She injected a note of hope into the statement.   I almost believed her, almost bought into it.



But I shook my head.  ``Kind of, but kind of not?''



``People were talking about it, asked if I'd fight, and they encouraged me and stuff, but when I said no, they started talking among themselves, and it didn't sound so hot.''



``No.  I'm thinking it probably isn't so hot.  You're right.  There are reasons to fight, and saving humanity isn't necessarily the sum of it.''



``Selfish reasons,'' she concluded.



I nodded.  ``Pride.  Revenge.  Sheer stubbornness.  I like stubbornness.''



She nodded, but she didn't respond.



``Why aren't you fighting?'' I asked.  Then I raised a hand, stopping her before she could speak.  ``Sorry.  That came out like an accusation.  I only\ldots I meant it out of curiosity.''



``It's okay.  I might deserve the accusations.  I'm not a fighter.  Like, at all.  Besides, what could I do?  Girl with a good voice.''



I shook my head.



Voices.  I thought about it.  How many capes had I run into with eerie or altered voices?  I'd had the beginnings of a thought while talking to some kids  back in my first days among the Chicago Wards.  Cricket, Rachel, Labyrinth, Night, Oni Lee, Mannequin and others I couldn't be bothered to think of, had had their voices or their abilities to communicate either removed or altered irrevocably.  Leviathan, Scion, the other Endbringers, they didn't speak either, but they weren't quite human.



Me, Grue, Eidolon, Glaistig Uaine, Dragon, Defiant, Bakuda, \"{U}ber, Canary\ldots we'd all used powers or technology to manipulate our voices, had done it as a matter of habit.  A lot of us were powerful capes, others were minor capes striving to look more important.  Odds were good I fit in \"{U}ber's position, more than Eidolon's.  I could guess that Canary was in the `low power' category as well, but I didn't know enough about her.  Bakuda was hard to place, but I suspected her power was devastating, and her lack of success was due to the chassis the power had attached to.  An unstable, unpredictable individual, too intent on terrorism to become as big as her power deserved.



\emph{Damn}, we could probably have used some of her best work.



Was there something important in that jumble of stray thoughts on voices and communication problems, or was my mind wandering in vain attempts to avoid thinking about how bad things were?



\emph{Communication}.  The word crossed my mind.



Tattletale entered the room through the door to Canary's left.  Rachel and Aisha followed, with Bastard and another dog trailing behind.  Tattletale carried a pile of clothes, neatly folded and stacked.



``Tailored to your measurements.  I wasn't sure if you'd be keen on getting straight into costume or not.  A lot of people aren't.''



``Thank you,'' I said, taking the clothes.



I didn't dress.  Instead, I stood by the side of the bed, holding the clothing.



They waited, as if apprehensive.  Aisha wasn't visibly upset, so I could assume Grue had gotten out.



I sighed a little.  ``How bad is it?''



``We lost just about half of everyone,'' Tattletale said.  ``Maybe more, but communicating's hard right now.  Don't exactly have an infrastructure.''



``Everyone being-''



``The capes, the civilians.  Everyone.  Half of Bet's onetime population is gone, just about.  Good news is he's traveling between possible Earths, hitting major population centers, so the individual incidents aren't doing so much damage on a \emph{relative} level.  Bad news is he's traveling between possible Earths.''



I tried to process that, then gave up.  ``How many possible Earths are there?''



``Not as many as there should be,'' Tattletale said.  ``Technically, every action should create a world where that action came to pass.  Best guess is that he compartmentalized everything.  Limited how far we could roam so he could save the other Earths for\ldots \emph{something}.''



I nodded slowly.



``We're in bad shape,'' Tattletale said.  She offered me a sympathetic half-grin, as if she'd just told a joke she knew was bad.



``We're doomed,'' Aisha added.  ``The dog is fucked.''



Rachel wrapped her arm around Aisha's neck, seizing her in a headlock, wordless.  Aisha struggled and squeaked, while Rachel maintained the hold, not so tight as to choke, but tight enough to be uncomfortable.



I looked pointedly at Canary, as if to say, \emph{I told you they'd be blunt}.



Tattletale followed my gaze.  ``Refugees.  We're forced to keep moving, split up and spread out because of limited resources, and to minimize the damage when any one location gets hit.  Canary was a refugee from another group.  She wanted a place to stay, I offered.''



``Canary said people are still fighting,'' I ventured.



Tattletale didn't budge an inch.  A poker face.  Aisha's expression, by contrast, gave it away.  Pained, concerned, looking to Tattletale for validation.



``No?'' I asked.



``Yes,'' Tattletale said, but she didn't look confident.  ``Except it's not Scion they're fighting.''



I'd heard of someone's heart skipping a beat, had read about it enough times, but this was something else.  It was more like missing a stair and hitting the ground floor a little too hard, a thud in my chest.



So many things that could mean, none of them good.



Tattletale tucked her hair behind her ear, a tell, and then pointed at the door.  ``Easier to show than to tell.  Come on, Canary.''



``I don't- I'm not sure I want to know,'' Canary said.



``You're going to find out one way or another.''



Canary didn't budge.



``Okay.  Whatever,'' Tattletale said.  She glanced at me.  ``I'm gonna pull up all the relevant files, so this won't be five seconds of explanation with thirty seconds of searching between each bit.  Come whenever you're dressed and ready.  If you want to get her to come along, it probably wouldn't hurt.''



I nodded.



Tattletale stepped out, and Rachel let her arm drop.  I was surprised to see Aisha there, a little flushed in the face as she fled.  She gave Rachel the middle finger on her way out, walking backwards through the door.



I almost started to close the curtain for privacy, then realized I didn't give a damn.  I began pulling on the underwear.



``Are you going to try to convince me to fight?'' Canary asked.



``No, I don't think so,'' I responded.  ``No point, is there?  Unless you want me to.''



``She's scared,'' Rachel observed.



``\emph{Everyone's} scared,'' I responded.  Rachel hesitated, then nodded a little.



Canary spoke up, ``What did she mean, it wouldn't hurt?''



I started putting on the skinny jeans Tattletale had given me, hiking them up beneath the hospital gown.  ``My guess?  Most of the people we lost were some of the best of us.  Team leaders, brilliant tinkers, people who've seen ten or more Endbringer fights.  People you've heard about in the news, people you grew up reading about in magazines or newspapers.  Heroes, villains, people who don't apply to either category, all gone.''



I watched her expression change, studied it.  Eyebrows raising, the movements of her eyes as she mentally processed the fact that people like Eidolon weren't around any more.



I continued.  ``\ldotsThey were the sort of people who'd go to the front line without hesitation.  Not sure how many we have left, but odds are good we're down to a select few.  Major players who were lucky, clever or tough enough to walk away, capes with crappy powers or powers that don't apply, and then rogues or new capes who aren't experienced in fighting.''



Gently, cautiously, I added, ``We need everyone we can get.''



``I\ldots I can't do violence.  Like, at all,'' Canary protested.  I turned my back to pull off the hospital gown and do my bra.  I noted a change in the coloration of my skin where the flesh had been regrown.



``It's easy,'' Rachel said, taking over while I was distracted.  ``You hurt people until they stop doing whatever it is that irritated you.  \emph{Taylor }kicked me in the head the first time we met, and she was way scrawnier than you are now.  I stopped doing what she hated me doing, setting my dogs on her.''



``No.  I mean, it's like, mentally, I couldn't do it.  I get sick at the sight of blood.  Besides, my power wouldn't affect Scion.''



``Probably not,'' I agreed, pulling on the strapless top with the string going around the throat.  I turned around.  I thought about what Doctor Mother had said at the last big meeting.  ``But the real question is, do you want to be there when the world ends, struck by the sudden realization that maybe, possibly, you could have done something to help?''



She stared down at her legs.



``Baby steps,'' I said.  ``I'm not asking you to fight.  Just\ldots come.  Listen to what Tattletale has to say.  Guilt free, just to go that far.''



``And then it's harder to refuse the next part,'' she said.



``I promise I won't ask you to do anything,'' I said.  ``Strictly volunteer stuff.  If nothing else, think of it as a morale thing.  I'm using my bugs to feel out the surroundings, and the building is damn empty.  I'd feel a hell of a lot better about this if we had just one more body in the room.''



``A morale thing.''



I nodded.



``Okay.''



I grabbed the heavy jacket Tattletale had included and pulled it on.  If we were going anywhere Scion had been, odds were good it'd be cold, much like Earth Bet had been on our last visit.



We made our way out of the little room with the beds.



Tattletale had set up a command center.  The bulletin boards, the notes, the files, books and more had all multiplied tenfold.  She must have moved me closer to home, so I could be watched.



Aisha was with her, sitting on the edge of the desk.



``Bitch,'' Tattletale said.  ``Can-''



``I'll go patrol,'' Rachel said.



Tattletale nodded.



She turned one of her computer monitors our way as we approached, so we had a clear view.  When she started the clip, the same video showed on each of the monitors on the desk.



``Video feed from a cape called Greenhorn.''



``I know him,'' I said.  A new member of the Wards, having joined just before the Slaughterhouse Nine reappeared.  Untrained, he'd deigned to wear Defiant's combat calculation suit.



The image played out.  It took me a while to realize what I was looking at.  A crowd of refugees, fleeing into a portal.



The camera panned as Greenhorn turned his head.



Faultline was there, along with Dinah, Gregor, Labyrinth and Scrub.



Tattletale waited, then paused the image.  She tapped the screen.



I glanced at the image, but I didn't see anything out of place.  People in the crowd, tired, worn out.  A middle-aged man with a group of male teenagers and other men aged twenty to thirty.



``I don't see it,'' I said.



``You will,'' she said.  She resumed the video.



I watched the man she'd pointed out.  Familiar, but not overwhelmingly so.  Nobody I \emph{knew}.



The crowd flowed through the portal as a mass.  Up until the man I was watching stopped, turning around.  The men and boys from the group around him did too.  They became obstacles, standing against the stream of bodies.



``Far left,'' Tattletale said.  ``Recognize him?''



I looked.  A tan young man with dark hair cut close to his head.  He was perched on top of a thick wooden sign, his hand on a taller man's shoulder for balance.



``No, I said.



``You only saw him without his mask a few times,'' Tattletale said.



He was a cape?  I thought about it.  How many capes had I seen without a mask on?  Someone I'd seen while in Tattletale's company, or who Tattletale would know I'd only seen a few times?



It clicked, but something was already happening on the image.  Greenhorn was standing on the same side of the portal as the group.  Then he wasn't.  The image had shifted, and he was standing by other Wards and Protectorate members.



The image whirled as Greenhorn spun around.  He had been moved outside of the portal.



The man Tattletale had pointed out raised a device over his head, then hit a button.



The portal disappeared.



I watched as Labyrinth and Scrub stepped forward to try to knock open another portal.  They succeeded, but their efforts apparently didn't allow access back into the same world.



It was Teacher.  One of the cell block leaders of the Birdcage.  He had the ability to make others into thinkers and tinkers, but it left them extremely suggestible.  He'd surrounded himself with these mooks, then, what, he'd shut himself into another world and barricaded the door?



The cape Tattletale had pointed out would be Trickster, ex-leader of the Travelers, apparently one of Teacher's brainwashed minions.



The volume had been turned almost all the way down, but it hadn't been muted.  I could hear the faint cries of the crowd, see Greenhorn moving to stop them from rioting.  The looks of desperation, the fear, the panic, at realizing their way out had just been denied them.



The camera moved to Faultline.  She was talking, giving orders.



Labyrinth changed the `channel' on the portal, setting it to a different world.  The people began moving through again, a little faster, more forcefully.



``He betrayed us?'' I asked.



``No idea.  Maybe he wanted a safe place to work on a trump card with zero distractions.  Going by his modus operandi, though, yeah, I think he betrayed us.  Not a big betrayal, but that's one world where we moved a hell of a lot of supplies in''



I nodded, pursing my lips.



``Saint's upset, to put it mildly.  We ran the data.  Apparently he crossed paths with Teacher at some point a few months before Teacher's incarceration.  There have been almost no cases where Teacher's power lasted more than a few days without a refresher, and the brainwashing wears off over a few weeks or months, so yeah.  It's not that.''



``Saint wants something from Teacher?  A power?''



``Probably.  Anyways, Teacher had a few of those devices made.  Four portals in all that particular interest groups claimed and locked down, using these switches, wanting worlds all to themselves.  No major players in the bunch, no sign of any greater conspiracy.  Defiant was all too happy to bring Saint into custody, and we're kind of hoping to get a response out of the man.  That's problem number one.''



\emph{Number one}, I thought.  I felt a sick feeling settling in my gut.



``Number two.''



The video played.  Not a camera anyone \emph{wore}, but a steady image that panned left and then right.  A surveillance camera.  The scene was of a settled area.



Silent image, but the detonations were so vivid, so violent, I could imagine the noise of it, that crashing sound that would be followed with dead silence after the shockwave blew out eardrums.  Ten or twelve explosions at different points across the camera's field of view.  Coordinated strikes.



``Y\`{a}ngb\v{a}n,'' Tattletale said.  ``Refused to let Faultline or Cauldron open up any portals in the C.U.I. territories, and then the moment things got ugly, they invaded the portals others made instead.  Striking American settlements.  Including ours, potentially.  Part of the reason for Bitch's patrolling right now.  Wouldn't mind you doing a double-check of the area with your bugs, when you're up for it.''



I nodded slowly.



``Number three.  No video, so you'll have to take my word for it.  Cauldron.''



``You said they tried something,'' I said.



``You overheard.  Yes, but that's not what this is about.  It's the Irregulars.  They're actively fighting Cauldron, despite Cauldron's extensive resources, and they haven't been wiped out or assassinated.  Arguably the strongest precog out there, arguably the strongest clairvoyant, countless other resources, and they're actually stressing Doctor Mother out.''



``How?'' I asked.



``Hard to say.  Could be that Cauldron made a mistake, let a case fifty-three with a powerful Stranger ability slip through the cracks, and Weld recruited him or her.  Could be a disgruntled customer.''



``Disgruntled?'' Aisha asked.  ``Fun word, makes me \emph{gruntled}, but I don't follow your meaning.  Superpowers for cash instead of powers for trauma\ldots how is anyone not cool with that?''



``Maybe Canary could shed light on this?'' Tattletale suggested.



Canary's eyes opened wide.



``You bought Cauldron powers?'' I asked.



``Yes.''



``Pretty rare for a natural cape to get powers with physical changes,'' Tattletale said.  ``Cauldron capes?  Yeah.  You definitely see stuff like feathers.''



``I wasn't disgruntled,'' Canary said.  ``I freaked, and I couldn't exactly charge back on my credit card or sue them.  But I adjusted.  I got what I really wanted in the end.  By the time I realized I'd gotten \emph{too much }of what I wanted, I was already in jail.''



``Shit sucks,'' Aisha said.  ``Scammed hard, grow yellow feathers on top of a shitty fashion sense, get what you want and then boom, it's all over.  Off to jail.''



``I dress colorfully so people don't connect me to the Simurgh so easily,'' Canary said.  ``Keeps me from getting cussed out or beaten by someone who lost a friend or family member.''



``Getting back to the question, with all of the issues you've faced, you could see where someone else would be less cool about it, yeah?'' Tattletale asked.



Canary nodded.  ``Um, definitely.  The stuff they give you isn't always reliable.  You're always gambling, whether it's on the amount of raw power, the nature of the power, all of that crap.



``And if someone like Weld showed up, saying he has contacts in the Protectorate and the Wards, good friends, who told him they've got a way to break into another universe if they can find a spot where a portal was opened, and they just need you to tell them where Cauldron opened one?''



``They stepped through into my dad's house once, so I could talk to a therapist before I took anything.  Yeah.  If things had gone differently, I could have pointed them to the right place.''



``Another possibility for how the Irregulars are managing,'' Tattletale said, sounding satisfied.  ``With Contessa and Cauldron's other hit squads being too busy with more important matters to retaliate.''



I nodded.  It wasn't \emph{sound}, but there was enough there for me to acknowledge it was very possible.



``Issue number \emph{four}.''



``Wait,'' I said.



Tattletale paused.



``This is a thing?  There's a pattern here?''



``Isn't it obvious?  I mean, you can connect the dots.''



I could.



``You said it before,'' Canary told me.  ``Remember?  There are reasons for people to fight, reasons to keep going when all is lost.  Pride, revenge, stubbornness.''



``Fuck me,'' I said.  I stepped back, leaning against the wall.  The blunt ends of tacks poked me in the back and shoulders where I leaned against a bulletin board.  ``\emph{Fuck!}  They're all fighting, and they're not fucking capable of turning this aggression towards \emph{Scion}?  What the \emph{fuck}?''



Tattletale shook her head.  ``Scion trounced some of our strongest capes and as far as we can tell, we didn't even slow him down.  We only gave him the bright idea of attacking other Earths, buying our world a few days at most, but we screw over a trillion other people in the process.  Might be they want to do something that \emph{isn't} futile, before humanity gets wiped out.''



I hung my head, and my hair fell forward.  I clenched my fists, and I could still feel the alien sensation in my hand.  I rubbed my fingers against the palm.



``I'm going to keep going, just so you know what's up,'' Tattletale said.  ``Issue four.  Elites, Vegas Dark, less pleasant members of the \emph{Thanda}.  We've got the businessmen and bastards of Vegas's underworld, guys who were already gaming the system, only now they're moving into refugee locations on the far sides of the portals and trying to elbow their way in while things are just starting up.  Hoping to make themselves a fixture like \emph{we} made ourselves fixtures, so everything grows up around them, dependent on them.''



I nodded, feeling just a touch numb.  ``I don't need in depth explanations.''



``Fine.  Five?  Sleeper on Zayin.  Six?  Warlords on Bet, preying on those who decided not to leave.  There's shit sprouting up all over, so maybe I could save issue \emph{seven} is everything else put together.  We could get wiped out under the combined weight of a thousand lesser issues.''



``Not a problem,'' Aisha commented, her tone ironic.  ``Easy peasy.''



I stared at the screens.



Tattletale studied me, then added, ``The Simurgh showed up on Bet, but there's nothing really left for her to destroy,'' Tattletale said.  ``There's refugees, people who didn't leave, holed up here and there, but she doesn't seem to care enough to go after them.  She's\ldots still.  A non-threat, at least for now.''



``It's too early for her to show up,'' I said.



``They're attracted to conflict,'' Tattletale replied.  Answer enough.



``It's funny,'' Aisha observed, ``In this really sad, demented, `everything sucks' way.  `Oh hey, here to destroy everything\ldots oh, is everything already destroyed?  Shit, fuck.  Guess I'll hang out, dick around over here while humanity winds down like an unwound clock that some golden asshole is stomping into little pieces'.''



``Your metaphors tend to fall apart,'' Tattletale observed.



Aisha shrugged.



``People have given up, then,'' I said.  ``We mustered our strength, gathered some of our best, and he took us down.  He killed one of our strongest.  So now they're focused on petty things.  Even if we could fix it all, we've still got the Endbringers and Scion waiting to systematically murder us all.''



``All of the great things humanity's done,'' Canary said, ``Innovation, society, great works of art, the music\ldots  I kind of hoped we go out in some noble way.''



``I don't think humanity is noble,'' I said.  ``Not in the least.  It's not just or fair on an intrinsic level.  It's not even \emph{good}.  But I kind of hoped we'd go out fighting the other guy.  Dinah said Scion would take out just about everyone, leaving anywhere from a few billion to a few hundred still alive.  Probably the people who've scattered far enough apart it's not worth hunting them down.''



``Probably,'' Tattletale said.



``Looking at this stuff, hearing you describe it all, I'm starting to think that maybe we'll destroy ourselves in the end.  Infighting, stupidity, revenge, all of that.  Humanity will clean up whatever members of humanity Scion leaves alive, or leave us too screwed up to bounce back.''



``Ergo, the dog is fucked,'' Aisha murmured, barely audible.



Tattletale snorted a half-laugh, despite herself.  That, in turn, made me smirk stupidly.



Tattletale saw that, and she laughed a little, which started \emph{me} going.



Aisha joined in.  Not a full belly laugh, but a giggle fit, all the more infectious because of how out of place it was.



I glanced at Canary, who was looking at us like we were batshit insane, and that only started me going again.



It took us a minute or two to stop altogether.



``Where the hell did you learn a word like \emph{ergo}?''  Tattletale asked.  I had to bite my tongue to keep myself from laughing any more.



Aisha shrugged, smiling a little.



``So.  Want to join in on the petty shit?  Anyone in particular you want revenge on?''  Tattletale asked.  ``Aisha?  Taylor?  Canary?  Feel free to speak up.  No judgement here.''



``I'll judge you a teeny bit,'' Aisha said.



``No,'' Canary said.  ``Don't want any revenge.  Like I said, I'm not big on violence or any of that.''



``I'm not one to put off revenge,'' Aisha said.



``What about the bullies?''  Tattletale asked me.



``I made peace with that some time ago.  No petty shit I'm that invested in.''



Rachel had returned, tying her dogs up outside.  I followed her with the bugs that clung to her as she made her way inside and upstairs.



``Want to go get laid?''  Tattletale asked.  ``Seems like something people tend to do in the movies, when the end is nigh.''



``Were you just inviting Taylor or-''



Tattletale swiveled in her chair and kicked Aisha in the shin.  ``\emph{No}.  I'm not interested in that kind of thing.  My power makes it way less fun than it ought to be.  Information overload during sex is squick.''



``Sure,'' Aisha said.  ``Sure.''



Tattletale kicked at her again.  Aisha only cackled.



``No,'' I said.  ``I've enjoyed that sort of thing, but that was more to do with who I was with than anything else.''



``Ew, ew, ew.  TMI.  Unless you're talking about someone else.  Tell me you're talking about someone else.''



``No.''



``Ew, ew, ew.''



Rachel entered the room.  Bastard was bigger than an ordinary dog, smaller than a pony.  He followed her, the collapsed on a pile of sheets in one corner of the room.  He heaved out a sigh.



``Welcome back,'' I said.



Rachel nodded.  She surveyed the room, taking us all in.  ``You're all in a good mood.''



``Just having fun,'' Tattletale said.  ``End of the fucking world, people are stupid beyond belief.  It's at the point where you can either laugh or cry, and I promised myself I wouldn't cry a long, long time ago.''



``Mm,'' Rachel grunted.  ``Right.''



\emph{Never been one to keep a conversation going}, I thought.  Rachel stopped at the end of the desk opposite Aisha.



I took a step to my left, and I sort of bumped my arm against her arm, smiling a little.  She bumped me back.  She didn't smile, but she put an arm up around my shoulders and set her hand on my head, mussing with my hair, like she had earlier.



``We were talking about what we'd do,'' Tattletale said.  ``You got any boy toys, Bitch?  Any way to scratch that particular itch?''



Rachel shook her head.



``Where's Grue?''  I asked, all of a sudden.



``Ew, gross.  Can you \emph{not} make those obvious leaps in logic?''



``He's gone,'' Tattletale said.  ``He was here while Panacea put you back together.  When, um, she was working on you, he borrowed her power and took over for a bit.  I don't know if you're going to see that as weird or gross or a weirdly sweet goodbye gift or deeply invasive or whatever, but yeah.  Maybe he just needed to help.  Needed to know that he could save you or help you or fix you after you'd fulfilled one of his old fears and gone and got yourself murdered in a fit of recklessness.''



``And then he left?''



``Retired, quit.  Maybe losing the fight, verifying he couldn't do anything constructive, it took something out of him.  Seeing you like that, it took something else.  And then he ran into Bonesaw.''



``She didn't work on me?''



``No.  We didn't let her.  She's paired up with Panacea for now, because Panacea is really the only way we can double check her work.  Anyways, yeah.  Grue confirmed you were on your way, he was leaving, she was walking in.  They crossed paths.  I think it was the straw that broke the camel's back.  He left without a word.  Cozen came by, asking if we had a spot they could head off to.  I sent them to a cabin we put a bit out of the way.  Generator, toilets, books, movies, insulation.  Pretty sure it's just the two of them, taking care of each other until the world ends.''



I drew in a deep breath, then exhaled.



I couldn't bring myself to feel envious, jealous or upset.



``Okay,'' I said.  ``Good.''



Tattletale nodded.



I thought about the others.  ``Parian, Foil?  Are they keeping each other company too?''



``Of course,'' Aisha said.



``Says our resident voyeur, a touch too knowingly,'' Tattletale said.



``That was the \emph{one time}!  Which wasn't even fun voyeurism, because it was my \emph{brother}.  And I didn't say it knowingly \emph{at all}.''



``The lady doth protests too much,'' Tattletale said.



``I'm protesting exactly enough and fuck you!  Like you're not privy to the sordid details of other people's lives.''



``Privy?  Sordid?  So soon after \emph{ergo}?  Have you been \emph{reading}, Aisha Laborn?''



Rachel nudged me.  ``They were helping with the patrols, watching for the gem-faced motherfuckers who're probably going to cause trouble.''



Oh, she was answering my question about Parian and Foil.



``Gem-faced motherfuckers?  The Y\`{a}ngb\v{a}n?''



``Them.  So the other two are around.  They're here for work but they don't really hang out.  They're better at dealing with people than I am, so they do that.  Investigate shit.  I'm the one that drags the assholes back here.''



``Sheriff of New Brockton Bay,'' I said, speaking just a little louder to be heard over the others.



``\ldotsfucking words because of \emph{you}.  Talking funny, trying to sound smart\ldots''



``You said something like that,'' Rachel told me.  ``Before you left.''



I nodded.



``Sorry about that,'' I said.  ``Leaving.''



``Okay.''



No forgiveness, but then again, I probably didn't deserve it so easily.



``I'll be back,'' I said.  ``Have to go.''



Rachel nodded.



I made my way to the bathroom to relieve myself, then took a minute to wash my hair and try to comb my hair into a semblance of order.  Try being the operative word.



Two days, at least, I'd been out, probably three, if I judged by the state of my hair.  Rachel rubbing my head hadn't helped.



I took a deep breath, then exhaled.



I made my way back to the others.  Tattletale and Imp had stopped bickering.



We settled into an easy silence.  It was a sort of quiet state I'd found with Rachel, but it was rare to have with any of the others.  Rarer still with Imp.



As memories went, for bringing everything to a close, it was alright.



It was the outsider who broke the silence.



``This is us?''  Canary asked.  ``We're whiling away the time until the world ends?  Giving up like everyone else?''



``What?''  Tattletale asked.  She gave Canary a funny look.  ``No.  Fuck no.''



``No,'' Aisha said.  ``Wait, did anyone think that?  Because I was thinking this was more us trying to decide what the hell we need to do before we throw ourselves into one final, suicidally reckless attack.''



``Basically,'' I said.  ``Minus the suicidally reckless part.  There's other stuff we can try first.  But yeah.  I think we're mostly on the same page here.''



``Go out fighting,'' Rachel said.



``Go out fighting, '' Tattletale confirmed.



``Nothing held back,'' I added.  ``Right.  I'll need my stuff.''



``Put the pack and what's left of your costume aside.  I can go get it anytime.''



I nodded.



``We'll need help,'' Tattletale said.



``Parian and Foil?  Can we get them onboard?''



``Probably, if we can come up with a convincing argument.''



I nodded, thinking.  ``What about Shadow Stalker?  Any idea where she is?''



``She's around.  You think you can convince her?''



``We'll see,'' I said.



``We need a plan, first and foremost,'' Tattletale said, ``If we've got one, we'll be able to get others on board.''



``There are possibilities,'' I said.  ``Need to knock some heads, get people on board, get morale up.  Fix some of the crises that've come up, deal with the people who are fucking the system and making everyone else think there's no hope.''



Tattletale glanced at me as if I'd said something that provoked a thought, and then she smiled.



I couldn't help but feel it wasn't a real smile.  Her poker face.



``You coming, Despairy Canary?''  Tattletale asked.



I could see the hesitation cross Canary's face.



``Yeah.  I'll come.  Might not be, uh, knocking heads, but maybe there's something we can resolve with my power.  Nonviolent resolution.''



``With a song and dance number,'' Aisha said.  She leaned forward and took hold of Canary's hands.  ``Like a kid's movie!  Sing a song and fix problems!''



``Um,'' Canary said.  She looked between Tattletale and me.  ``How am I supposed to respond to that?''



``Just ignore me,'' Aisha advised, adopting the demeanor of the veteran bestowing wisdom onto the novice.  ``Everyone else does.''



``I guess I'll try.''



We gathered ourselves together, and we began making our way downstairs in two groups, with Aisha still holding Canary's hand, leading the way.  Tattletale, Rachel and I followed.



My body still felt weird, but the alien sensations weren't as pronounced.  I was getting used to it.



``Thanks for looking after me,'' I commented.



``Not a problem,'' Tattletale said.



``Before, you were bluffing.  Can I ask?  It changes how I deal with this.  How much I give it, the risks I take.  Can you tell me honestly that this isn't hopeless?''



``Honestly?''  Tattletale asked.  She trailed off.



Answer enough.



I glanced at Rachel.



Tattletale practically seemed to read my mind.  ``She doesn't give a damn.''



``I don't give a damn,'' Rachel echoed.



I nodded.  ``You've been wrong before, Tattletale.  About important stuff.''



``I have.  See, this is the part where I can either lie to you or tell you the truth.''



``Truth.  If it doesn't spoil the mood too much.  I don't want to hear, like, Dinah said a hundred percent chance we're wiped out.''



``Nothing like that.  But there's evidence.  Enough for me to connect dots.''



``You're talking about the kid that speaks funny,'' Rachel said.  ``The fairy whatsit.  You were watching her video.''



Tattletale sighed.



``What?''



``There's moments I adore you, my adorable canine crusader, and there's moments I hate you.  All too often, they're the same moments.''



``Whatever.''



``And that there is another case in point,'' Tattletale said.  She smiled, looking at me.  ``So yeah.''



Weaver or Skitter would have pressed for the truth.  During the Echidna incident, I'd gone to great lengths to strive for honesty and full disclosure.  Had it worked out?  Maybe.  Maybe not.  It had meant a lot right then, but it had sort of screwed me after I'd surrendered to the PRT.



But \emph{Taylor}?  \emph{Taylor} had lived a lie, had spent some time wallowing in ignorance.  Ignorance of what Tattletale really knew, ignorance of what Coil was doing.  Ignorance of what real monsters were capable of.



And then I'd donned the mantle of Skitter, I'd become the warlord.  Later, I'd gone on to become Weaver, where I felt less like myself than ever.



The Taylor days had been some of the best days, in a way.  Not my greatest moments, but some of my most cherished ones, yes.



``Do I need to know, Tattletale?''  I asked.  ``For this?  Does it provide any crucial information, for dealing with any of the stuff we've got to deal with?''



``Yes,'' she said.  ``But probably not right away.''



``Okay,'' I said.  ``Then I can wait.  Let me enjoy some blissful ignorance for just a little while longer, while we make our way out there, try to save the world from itself, if not from Scion.''



``Deal,'' she answered.





