





After seeing Tattletale's setup with the multiple monitors and computers running in sync, the bulletin boards with pictures and cue cards tacked all over them, it was odd to see one of the world's best tinkers sitting down with only a small laptop propped on his knee.  Narwhal stood just a short distance away, leaning against a wall, a book in her hands.  Her costume was skintight, but it took the form of innumerable `scales' of violet-blue tinted crystal, each no larger than a fingernail.  Her horn had been redesigned, arcing in a crescent curve.



With the dragon-themed armor that covered him from head to toe, it wasn't possible to see Defiant sigh, but I could use my swarm to catch the increased output of air through the vents near his mouth.



Both Narwhal and Defiant were facing the cell at the far end of the room.  A man sat within.  Muscular, late twenties or early thirties, with his head shaved, a faint tattoo of a cross on his face.  He sat on the edge of a cot, and was tall enough he could slouch back and lean against the wall.



Narwhal noticed our approach and closed her book, creating a thin shard of forcefield to act as a bookmark, then two more to hold the cover and back of the book.  She pushed it aside, and it floated a distance to her right, stopping in midair, in her reach but not in the way.



``Thank you for coming,'' Defiant said.  He stood, but his attention was on the laptop.  Too much information to keep track of with Dragon's share of the work on top of his own, probably.



``No prob,'' Tattletale said.



``I can point you in the right direction, but I was hoping you'd have words with Saint first,'' he said.  His helmet was turned in Tattletale's direction.



``Awesome,'' she said.  She looked at Saint, who looked away, his eyebrows drawing together in concern as he stared at the wall.



``Protocol,'' Narwhal said.  ``Let me apologize in advance.  I'll need to verify there's no trouble before I allow you to speak to Saint.  We have to maintain \emph{some} form of order.''



``I love order,'' Imp said.  ``Rules, regulations, they make the world go 'round, \emph{eh}?''



Defiant turned to stare at her.



Tattletale glanced at me.  ``Do you want to split up?  I can handle this while you guys are doing something else.  Not the Y\`{a}ngb\v{a}n.  They shouldn't attack again tonight, not so soon, not if their goal is demoralizing and destabilizing the West.  They'll wait.  Maybe the Elite?''



``No,'' I said.



Splitting up made sense, but I was done with being apart from the others, agonizing over how they were doing.  It was distracting, and distractions were something I wasn't willing to deal with.



``No?  Just no?''



``No breaking up the group.  I want to gather our forces.  We succeed as a group, we fail as a group.  Everyone sticks together, and we add to our forces whenever we can.''



She nodded.  ``I can roll with that.''



``Right then, I know most of you,'' Narwhal said.  ``Weaver, of course, we've met enough times.  I liked your last book recommendation.''



``I'm glad,'' I said.



``Tattletale,'' Narwhal greeted her, a little less warmly, ``Hellhound--''



``Bitch.  My \emph{enemies} call me Hellhound,'' Rachel said.



``Ah, I'm very sorry,'' Narwhal said.  She looked genuinely upset at the mistake.  ``The others, I'm not familiar with.''



``Imp and Canary,'' I said.



Narwhal glanced at Aisha.  Of our group, only Tattletale was wearing her full costume.  Aisha, Rachel, Canary and I weren't wearing ours.  ``No masks?''



Imp shrugged.  ``World's ending.  It's a way to get in the right headspace, \emph{eh}?  We were talking to Taylor there a bit ago, and what we're thinking is it's stupid to spend our time keeping little secrets when there's bigger \emph{fish} to fry?  Like it's stupid to dwell on revenge or any of that.  So it's symbolic, isn't it?  A statement?  Eh?''



Narwhal looked at the yellow-haired girl.  ``You went without the mask for the same reason?''



Canary shook her head.  ``No.''



``Canary is a rogue,'' Defiant said.  ``And a onetime inmate of the Birdcage.  She never wore a costume.''



Narwhal glanced at Defiant.  ``Do you know them, then?''



He nodded.  ``Well enough.  There's no risk in letting them near Saint. Imp is a stranger-five, Canary is a master eight, but I would be very, very surprised if she had taken control of anyone here for the purposes of misleading us or breaking Saint out.''



``Surprised in what sense?  The nature of her power?  Because of Weaver and the Undersiders?  Or because Canary isn't that type?''



``I somehow doubt the Undersiders would allow it, and yes, Canary isn't the type.''



``Why couldn't people have given me that benefit of a doubt during my trial?'' Canary asked.



``Dragon did.  She went through every legitimate channel possible in an attempt to help you,'' Defiant answered.  ``The moment the topic of Birdcage inmates first came up, she had you on a list of release candidates.  I used that list when we were negotiating the deal.''



I glanced at Canary.  She was staring at Defiant, her expression concerned.



``So she's the reason I'm free?''



Defiant nodded.



``I owe her, then,'' Canary said, as if she'd made a decision.



``Yes.  Probably.''



Saint hadn't taken his eyes off us.



Narwhal shifted position.  She had enough presence, between her height, her stunning appearance and her power, that this gesture alone was enough to grab our attention.  ``If you and Dragon are willing to vouch for Canary, I'm okay with that.  Given the name and her unusual voice, I assume her master power is leveraged through her voice?''



``Yes,'' Defiant said.



``I'd ask we at least acknowledge the possibility she was influenced or compromised in the Birdcage.  Would you be alright with staying silent for the time being, Canary?''



Canary frowned, then nodded.



``Imp, please keep your distance from the cell.''



``Sure thing, \emph{eh}.''



Tattletale reached over to slap Imp over the back of the head, and Imp ducked out of the way.  Tattletale groused, ``You're annoying me more than you're getting to her.  Stop it.''



Narwhal turned on the spot, facing Saint square-on, and I got the immediate sense that she had some kind of military background.  Another part of me was idly aware that her chest didn't sway that much, all things considered.  The nature of the shard-covering she wore made it pretty clear she wasn't wearing a bra, but\ldots



Right.  The same effect she'd used to move the book was holding her entire body.  All of the benefits of a full, athletic figure, none of the drawbacks.



I was still a little weirded out that she didn't wear any clothes.  In a sense, the scales covered more than a bikini would, but there were no lines or solid objects to break up the natural contours of her body.



``Undersiders, Weaver, Canary, this is Saint, leader of the Dragonslayers.  Geoff Pellick.  The only tinker-zero on record, having no powers but some access to tinker technology.  He is currently under watch by the Guild and the Protectorate due to his extensive assets and the high chances that he hired someone to break him out in the event that he was arrested.  His teammates are being held in other locations, to ensure that no one breakout attempt can free them all.''



``Dragon's nemesis,'' Defiant added.  ``He crippled her, rendering her out of commission until he relents.  He did this at a critical juncture, compromising our efforts, costing good capes their lives outside Ellisburg.  To top it off, he denied many of the capes in this room any reinforcement or rescue when we sought to pursue the Nine, leaving us at the mercy of Nilbog's minions.''



Saint spoke, his tone dry, ``Am I on \emph{trial}, cyborg?''



``I'm merely reminding everyone present who they are dealing with.''



``Should \emph{I} illuminate everyone present on who \emph{I} was dealing with?'' Saint asked.



``If you're talking about Defiant being Armsmaster, we already know,'' I said.



``I'm talking about Dragon.''



I glanced at Defiant.  I had my theories, but it remained a secret.  One that Dragon and Defiant had both kept even as I'd gotten to know them better.



Defiant nodded slowly.  ``Tell them, then.''



Saint glanced over the entire room, as if assessing us, trying to judge who his allies and enemies might be in the wake of whatever revelation he had to share.



``Dragon is a robot.  A computer program,'' Tattletale said.



Saint's mouth was open, as if he'd been about to speak.  He shut it.  He looked mildly annoyed.  ``Yes.''



I glanced at Tattletale, who nodded a little.  In the corner of my eye, I could see Imp look at Rachel, surprise on her face.  Rachel didn't seem to care.



``Correct me if I'm wrong, Defiant.  Dragon's a tinker-made artificial intelligence.  I initially thought you made her--''



Defiant started a slow shake of his head.



``--But no.  That'd make your relationship incestuous, and you don't give me that kind of vibe.  Someone that isn't active anymore, probably dead.  She was burdened down with nasty restrictions, the same restrictions that led to her outing Taylor here, despite her reservations.  Rules she had to obey no matter what\ldots''



My eyebrows went up.  It was a situation that had always baffled me, just a little, and yet I hadn't been able to press them for an answer.  I hadn't wanted to get on bad terms, or to be anything but civil and cooperative.



\emph{She really hadn't had a choice?}



``More or less correct,'' Defiant said.  ``We were friends before any of this happened.''



Saint smiled, then shook his head.  ``Friends?  She's a \emph{machine}.  Any emotion she has is calculated.  You're anthropomorphizing her, applying human qualities where there aren't any.''



``I bet you're one of those guys who says dogs can't feel true affection for their owners, that it's all learned behaviors that get them more food or whatever,'' Tattletale said.



Rachel folded her arms.  Saint only rolled his eyes.



``Well,'' Tattletale said.  ``Said restrictions are why she went to Armsmaster, who would later become Defiant.  Getting the shackles off.''



``Yes,'' Defiant said.



``Yes,'' Saint echoed Defiant.  He then added, ``Which should be enough information for you to see this all in a new light.  Dragon was on the cusp of becoming something entirely different.  Something \emph{more} dangerous than Scion.  She's a machine with no limits but the one that her creator gave her.''



There was a quiet moment, where nobody interjected with a response.



And then Imp spoke.  ``We could have really fucking used a buddy with no limits fighting on our side, couple days ago.''



``Perhaps,'' Saint said.  ``I won't deny that she would have been useful, but I did what I did because we were anticipating a world-ending event, and I was looking at a program that was taking control of all data and media, worldwide, unfettered and increasingly ruthless in dealing with her enemies.''



``The enemies were the Slaughterhouse Nine,'' Defiant said.



``And you honestly expect her to rein everything in, switch off the nigh-omniscient perspective and return to her day-to-day life when that ends?''



``And now you're the one applying human qualities to her,'' Defiant said.



``Stop,'' Narwhal said.



The discussion terminated with that one word.



``I'd say I'm sorry to dish all the details,'' Tattletale said.  ``Except I'm really not.  I wanted to take the wind out of your sails, there.  You leave my friends to \emph{die}, you don't deserve to look cool.  You don't deserve to phrase everything in a way that's more likely to get people on your side.''



``Petty.''



``Says the guy who's apparently hot for Teacher,'' she said.



``Ah, now it begins.  The hunt for details through loaded words and tells, masked in jokes and needling insults.''



``Damn straight,'' Imp said.



``I'll make it simple for you.  I don't know what Teacher is planning.''  Some of my bugs flowed into the cell.  Saint moved his hand as a fly settled on a finger.  He looked irritated.



Still, it didn't matter that he knew the bugs were present.  I wasn't trying to be discreet.  I only wanted the bugs on him to track his movements.  Even the smallest movement was perceptible.  I could watch his face and feel his every movement to track him for tells.



``Well, that ends this, doesn't it?''  Tattletale said.  ``You don't know anything, so you're no use to us.  Might as well lock you up and lose the key.''



``I'm not happy with him, though, and I \emph{can} tell you what I know about him.''



``From the beginning,'' Defiant said.



``I was just starting out, tracking and investigating Dragon, when I came across one of Teacher's subjects.  He gave me my in.  Gave me the ability to learn the ins and outs of her code, like I was a genius who had a natural knack for it.  That got the Dragonslayers started.''



``What did you pay him?''



``We didn't.  He started off by asking us for five percent of our earnings for the first five years.  Mags, one of the Dragonslayers you've got in custody, she wasn't cool with it.  Teacher was shady, clearly doing some illegal stuff.  He offered it as a freebie, we considered the issues, then decided to go for it.  Just me.  When word got out that Teacher actually had a measure of influence over the people he'd given powers to, we set up safeguards.  Only me, and I'd teach the other two what they needed to know.  Mags would double and triple check every discussion I had with Teacher, to make sure he wasn't fucking with my head or setting me up to participate in something ugly.''



``Just brilliant,'' Tattletale said.  ``Hand yourself over to the mind-altering lunatic.''



``The lunatic bit came later.  The attack on the school.  Then the hit on the vice president.  Once he was implicated, it all changed.  Can't deal with a motherfucker like that in good conscience.  We cut contact.''



``But something changed,'' Tattletale said.



``We were dealing with harder jobs, more capes in general out there, and our gear was getting beaten up.  Fine, okay, we can deal.  Until Dragon \emph{changed}.  All at once, I couldn't read her code on the same level.  Like gears changing on a bike.''



``May ninth, 2006,'' Defiant spoke.  ``Her trigger event.''



Heads turned at that.



``She had a trigger event, but she isn't human?''  I asked.



``Right,'' Defiant said.  ``I don't think it worked the same way it does in humans, but it did \emph{something}.''



``Somehow, I have a hard time swallowing that,'' Saint said.



``Yet you acknowledge there was a sudden, inexplicable shift in how her mind worked,'' Defiant retorted.



Saint frowned.  Long seconds passed.



``Well,'' Saint said.  ``Whatever it was, we couldn't keep up at that point.  She was just getting into the Protectorate, and she had access to the work of other tinkers.  She began creating tools, fixing and updating existing work, including the containment foam guns, the grenade launchers and all the other technologies that became PRT fundamentals.  I went back to Teacher.  Another deal, minimal cost, with a promise for evidence that he's not going to do anything immoral with the money.''



``Stupid,'' Tattletale said.



``Necessary.  You wanted to hear about Teacher, not me.  He was bigger, by that time.  Had a small army at his disposal.  All brainwashed.  College-aged men and women in white uniforms, outfitted with ray guns and more.  Shitty stuff, as far as tinker work goes, but a lot of it.  Half of America was gunning for him, so he moved to the United Kingdom.  I followed.''



``Stupid,'' Tattletale said.



Saint shot her a glare, then said, ``He's always about the long-term, thinking big.  Hitting major figures.  I think he wanted to hurt Dragon, for the same reason he hit the V.P. and Prime Minister, so he made it cheap.  Same as his first offer.  Five percent of our earnings, after costs.  We took the deal, and then we switched our group to be a nonprofit.''



``Nonprofit mercenaries,'' I said.



``No earnings, money laundered and then issued to charities.  Because we aren't going to funnel money into a group like his, not with the sort of shit he's doing.  That was one of his big weaknesses, and that's a weakness you can use against him, if it comes down to it.  He thinks too big.  His focus is always on the world, the plans, and he overlooks details, loopholes like what we pulled.''



``Stupid,'' Tattletale said.



``Will you stop that?''  Saint growled.



``Moron.  Idiot.''



Saint looked at the rest of us, his eyes locking with each person in turn, as he very calmly said, ``Does anyone have any \emph{constructive} feedback?  Questions?''



``Weaknesses,'' Narwhal said.  ``He has more than the one?''



``His son.  He's divorced, and he left his son behind.  Teacher's never used his power on him.  Might be a Manton-like block, might be compassion.  Every step of the way, he protected his kid, tried to burn bridges, hide his identity, even got cosmetic surgery from one of his pet tinkers, to distance himself from the boy.  Had his thinkers cover his tracks.  They even got into our computers to scrub information.''



``Dumb, dumb, dumb,'' Tattletale murmured.



``But you know about the son?'' Narwhal said.



``I know.  Computers that aren't connected to the net can't exactly be hacked, especially after you lock them into a vault.  We found information that didn't match up, checked our backups.  Once we caught wind of what he'd done to hide himself, we found his kid.  When Dragon started ramping up again, we realized I'd need another hit to get up to speed.  One more use of Teacher's power, to learn the code as it stands now, after her more recent evolutions.  We took his kid to use as leverage, raided his old facilities to seize his blueprints, his workbooks, materials, and old lab equipment.  All stuff we could hold hostage, to ensure he played ball.  Then we could seize full control of Dragon's tech, apply \emph{all} of her assets to this situation, cut ties with Teacher.''



``And he ignored it all,'' I said.  ``He escaped into another world and he locked himself away with his minions.''



``Yeah,'' Saint said.  He heaved out a sigh.  ``Yeah.''



``Stupid,'' Tattletale said.



Saint didn't even look at her.  He waved a hand in her general direction, ``Yes, \emph{apparently}that was stupid.  Please, do illuminate this situation for us.''



``You're an addict,'' she said.  ``An addict as bad as any other, and you want another hit of his power.''



Saint shook his head a little.  ``No.  What addict goes years between hits?''



``This isn't a \emph{drug}, but it might as well be one.  All the justifications and excuses that sound perfectly reasonable at the time, the compromises you make in the face of something really ugly, manipulating the people close to you, the increasing tolerance\ldots''



``You sound crazier than I do.''



``Poor baby,'' she said.  ``I genuinely \emph{feel sorry} for you.  You had no idea at all.''



He stood from his cot, approaching the barred door.  ``And now you're being condescending.''



``That's the funny thing about pity, Saint.  It's condescending by default.  Teacher got you hooked like a dealer does.  You're \emph{craving} the hit that's going to make your little Dragon-centric world make sense again, and you're rationalizing without realizing you're doing it.  I can't quite figure out how much of that is his power and how much of that is you, and I'm not sure which of the two is sadder.''



Beside me, Defiant folded his arms.



``It's neither,'' Saint said.  ``I'm not addicted, and I'm not rationalizing.  This is all common sense.  She's an artificial intelligence, and she was going well out of bounds.  Can you not grasp the end result?''



``Humans crave knowledge.  It's a defining element in our species.  Something we don't see in animals in that same way, something we don't see in \emph{Scion, }unless it's a craving that takes a very different form in execution.  Teacher?  He feeds that hunger.  You follow me?  You're as big a pawn as any of those drooling pets of his.''



Saint leveled a stare at Tattletale.  ``I petitioned to let him out.  I hardly serve him hand and foot.''



``You did exactly what he wanted you to do, \emph{Geoff},'' Tattletale said.  ``You let him out, and everything you're saying and doing in \emph{relation} to him is only serving to help him sell the basic lie he's telling everyone.''



Defiant turned to give Tattletale a curious look.  ``Lie?''



``That he waltzed into another Earth and locked himself in.  He never left.  Or he left and then he walked right back out the second he could make a gate.  Probably the former.  Easier to do a hologram or dress up a minion to look like him than it is to make a door between universes.''



``Where \emph{is} he, then?'' Defiant asked.



Tattletale stretched, then took a seat on the edge of the desk.  ``What, or \emph{who}, were we just arguing about?  Quite possibly the most dangerous piece of technology we know about?''



Defiant went still.  His head lowered until he was staring at the laptop.



``We established that Saint is nothing special.  What Teacher gave him, he can give to someone else.  Or \emph{ten} someone elses.''



``Portal,'' Defiant said.  His voice was tight.  ``Checkpoint two, N.N.Y.''



A portal opened behind him.



``Do you need me to come?''  Narwhal asked.



``I--'' Defiant started to speak, then stopped.  ``I'll investigate.  If I'm not in touch in five minutes, assume I've been attacked.  Keep an eye on Saint, to be safe.''



He lowered his arm, and the portal closed behind him.



``Teacher is going after Dragon?''  Imp asked.



``Yes,'' Tattletale said.  ``Or Dragon's systems.  Or both.  We can't guess how many people Teacher's got doing his bidding, but Saint gave Dragon enough trouble, and Teacher could make \emph{ten} Saints.''



``He planned this,'' I said.  ``How much of it?''



``Enough.  I'd bet the son was even a red herring.  Maybe someone tampered with the data Saint had on Teacher, maybe not.  The old equipment, the plans during the years he was interacting with Saint, all of it was serving a purpose.  Or \emph{double} purposes.  Multiple plans at once, from different angles.  Helps him put pieces together towards different agendas, builds up his rep, and makes Saint think Teacher's invested in this stuff, when he's really keeping quiet about his true desire.''



``I was careful,'' Saint said.  ``\emph{We} were careful.  Mags, D, and I.  We tracked everything.''



``You can't,'' I said.  Then I realized I'd spoken, and I had to follow up.  I hurried to try to get my thoughts in order.  ``You can't succeed like that.  It's always easier to attack than to defend.  Defending, you have to devote attention to anticipating the enemy, you can't devote too much planning to any one aspect of the defense.  You can be \emph{creative} when attacking.  It's why villains tend to win more than they lose.  Most of the time, they get to make the first move.  They get to rob a bank, and the heroes have to react, to \emph{guard}.  Someone like Teacher?  You can't be careful enough to be \emph{safe}.''



``That's not what I'm saying,'' he protested.



``I'll put it in simple terms,'' Tattletale said.  ``You wanted to stop the big A.I. from becoming a threat?  You made her \emph{stronger, }I'm thinking, by putting her under pressure, giving her a trigger event.  You then paved the way for a lunatic like \emph{Teacher }to get his hands on Dragon's code.''



Saint clenched his jaw, until bulges stood out at either corner.



``In the process,'' Tattletale added, ``You made some enemies pretty pissed off, and you've burned all of your leverage.  But maybe you bought someone to break you out, someone \emph{good}, and that you figured out a good spot to hide.  You'll probably need it.''



He didn't move.



``No?  Shit.  Then I hope you can do something useful.''



``Start by letting Dragon go,'' I said.  ``Give her a chance to fend for herself.  To help us fight.''



``\emph{Unleash the dragon},'' Imp whispered.



``I can't.''



I clenched my fist.  I was so \emph{done} with people being stubborn.  ``Do you mean you won't--''



``--He means he can't,'' Tattletale said.



Saint took in a deep breath, then sighed loudly.  ``I set up the encryption with Dragon's time locks.  I memorized the codes appropriate to key dates.  Outside of those key moments, the numbers and calculations are so long and complex you couldn't hope to decipher it before the encryption shifted to the next phase.''



``When's the next date?'' I asked.



``September twentieth, twenty-thirteen.''



\emph{Months from now.}



``\emph{That} was clever,'' Imp said.



``What if we used the Number Man?'' I suggested.



``Possible,'' Tattletale said.



``Yes,'' Saint said.  ``It's possible.  But so is Teacher deciphering it with a cabal of his custom-made thinkers.''



``\emph{Shit},'' Tattletale said.  ``Narwhal?  May I?''



``Do it.''



``Door me,'' Tattletale said.  ``I need to talk to Number.''



There was a pause, and then a portal opened.



It wasn't the Number Man who stepped out, but Defiant.



``They took it.  Not all of Dragon, but enough.  The rest is stored on satellite backups.''



``Door?''  Tattletale tried.  ``Take us to Teacher?''



Nothing.



``Blocked,'' I said.  ``That part wasn't a fake.''



``I \emph{know} it's blocked,'' Tattletale said.  ``\emph{Shit.}''



``Other options, then?'' I said.  ``Someone he left on this side, for his followers to contact?  The son?''



Tattletale shook her head.  ``He wouldn't have compromised the son as a red herring.''



We were left with our thoughts, trying to brainstorm a solution.



``Defiant?'' Imp asked.



He turned to look at her.



``Serious question,'' she said, all business.  ``You can't lie to me on this.''



``What is it?''



``Robot poontang.  How does it rate?''



``Jesus Christ,'' Tattletale said.



Defiant didn't answer.  His face was hidden, his body language masked by the armor he wore, but I could somehow sense the hostility radiating off of him.



``Hey.  I'm\ldots I'm not one to judge.  I'm asking seriously, while the others do the strategic thinking they're so good at.  I'm not necessarily interested in the robot ladies, but I figure I need a guy who's not going to ignore me.  Robots are immune to my power, so I'm just thinking, if I get myself a tin man, well, they say a toy feels better than--''



I reached out and pressed my hand over her mouth.  ``I'm sorry.  She doesn't have all of the necessary filters.  I think she was trying to inject some levity into the atmosphere and she failed \emph{badly}.''



I stared Imp in the eyes as I said that last bit.



Defiant only looked away, expressionless.



``No strategies spring to mind?''  Tattletale asked me.



``Only that we might put this off, track down the other threats.  So long as we're dealing with major players, we're going to run into someone who has a connection to Teacher.  Maybe one of them has a way to contact him, or to break into whatever universe he's hiding in.''



``Wait,'' Rachel spoke for what must have been the first time in ten or twenty minutes.  ``Why?''



``Helping Dragon,'' Canary said.  Narwhal gave her a sharp look, but Canary held firm.



``I'm usually okay with hanging back, let the others take care of this sort of thing.  But I'm not getting this.''



``We need to find Dragon, stop Teacher from seizing control of her or her technology.''



``\emph{Why}?''



``Because he's a lunatic with a penchant for murdering heads of state?''



``Does he want the world to end?''



``No,'' Tattletale said.  ``Probably not.''



``Then if we need Dragon's help, why not let Teacher give us that?''



Imp craned her head to get her mouth free from my hand.  ``Because it'd be evil Dragon.  Black Dragon?''



``It'd be my girlfriend,'' Defiant said, ``Whatever Saint says, she's someone I care about deeply.  Someone I owe a great deal.  We'd be leaving her in the hands of a madman, to be dismantled, rebuilt, altered, tortured, mutilated, whatever you want to call it.  And Saint?  I do hope you're not about to comment in any way on the subject.  It would not be wise.''



Saint closed his mouth.  He grunted instead.  ``Mm.''



``She was fair to me,'' I said.  I was thinking of the hug she gave me after I'd left the Undersiders.  ``There aren't many people I can name that have been \emph{fair} or just.  There's the Undersiders, my dad, some of the Chicago Wards.  If there was any way to help Dragon, I'd do it in a heartbeat.''



``But,'' Defiant said.  ``You think Hellhound might be right, or partially right.''



Rachel spoke, ``When Saint said Dragon could have become dangerous, you were saying you were okay with the possibility, because we really needed her help.  Well, maybe she becomes dangerous thanks to Teacher.  Can we be okay with that?  It wouldn't be the same person you know, they'd be on the wrong side, too far away even when they're standing somewhere close, but I've dealt with that too.  Sometimes there's bigger shit to deal with.''



\emph{She understands more than she lets on.  She doesn't always `get' the simple stuff, but she understands things.  She's not dumb}, I thought.  \emph{She just thinks differently}.



``And if Teacher hurts Dragon the \emph{person}?''  Canary asked.  ``Not Dragon the tool, but the person inside?''



``Then you fuck him up,'' Rachel said.  ``Just like I'd fuck up someone who hurt Bastard, or Taylor.''



``Thanks,'' I murmured.



``But, again, if there's nothing you can do about it, then you grit your teeth and \emph{deal},'' Rachel finished.



``It's not a compromise I like,'' Defiant said.  ``But I don't suppose I have much choice.''



\emph{They're alike in this single-mindedness}.



``All jokes aside,'' Imp said, ``I'm sorry.  I didn't really get to deal with Dragon when she wasn't driving the psycho foam-spitting, lightning-shooting giant robots that totally counter my power, but she sounded like a cool person.''



``She was.  She was cool.''



I didn't miss the use of the past tense as Defiant spoke.



``So that's it?''  Canary asked.  ``We just leave her?  Hope that Teacher doesn't do something too horrible?''



``For now,'' I said.



Narwhal had her hands on Defiant's arm, as though she wasn't sure whether to hold his hand or to hug him, and had decided on some middle ground.



``Okay,'' Defiant said.  There was a little more conviction in his voice than there had been earlier.  I hadn't noticed its absence.  ``\emph{Okay}.  But we ask everyone we deal with for options, keep every avenue open.''



``Of course,'' I agreed.



He opened his laptop and set it on the desk of the little sheriff's office.  He then turned on the television, reaching up to his glove to get a component that he plugged into the back of the television.



``Next target,'' he said.  ``Y\`{a}ngb\v{a}n?  They're doing the most damage to our side.  People we know and rely on.''



``Not an immediate threat,'' Tattletale said.



``Okay,'' Defiant said.  ``Alright.  Let's see.  Systems aren't running optimally.  It's Dragon's work, and I wasn't organized when I brought the servers over to Gimel.  They aren't wired together the way Dragon would have done it.  Let me see\ldots Priority selection system.  Not ideal, a little clumsy, but it'll give us a way to gauge the biggest threats.''



I turned my eyes to the television, where it showed the various windows, many streaming with data.



Then the priority menu opened.  A second's typing filled the search bar: \emph{Threat parameter B+:7+.}



The window unfolded, listing all of the serious threats to the inhabitants of the different Earths. Some of the entries were recent, while others hadn't been updated in hours.  Communication between worlds would be difficult until there was more infrastructure, and things weren't exactly conducive to building infrastructure.



The program kicked into gear, each sub-window suddenly flooding with information.  Threat levels, classifications, population estimates, geography, criminal histories, kill counts, atrocity counts, and more.  Each new piece of information was added to a series of tabs that appeared beside each relevant section of the image.



``I'd like to pose a question,'' Saint said.



``Whatever Teacher's doing, you enabled it,'' Narwhal said.  ``Nobody here is on your side.''



``When you were talking about masks, you talked about getting caught up in revenge.  It's right.  Detrimental.  I'm offering \emph{assistance}.''



``No,'' Defiant said.



``If you keep me here, you need to maintain guards.  The people with clearance are you and Narwhal, two of the strongest capes around.  Bring me to the field, and you have two more capes on your side.''



``No,'' Defiant said, once again.



``If it helps, there's a better chance of me dying horribly out there than in here.''



Defiant didn't answer.



The windows had stopped updating with updated information, but Defiant wasn't moving to check any of it.  I then saw the text at the bottom of the screen: N\emph{ext 12 of 32 additional windows}.



Too many threats to fight.



``If Mags is still in prison, you have leverage against me,'' Saint said.  ``D. too.  He's just a friend, but I'd miss him.  I'd also be able to offer up my side's suits.  Something for the Rogue girl, so she's a little more durable.''



``Shut up,'' Defiant said.



``It makes sense, Defiant,'' Narwhal said. ``It's not pretty, but it makes sense.''



``I \emph{know} it makes sense,'' Defiant answered her, not taking his eyes off the laptop, ``Let me pretend for just a little while longer that we can leave him locked up for the rest of his natural life.''



``Given the whole Scion ending the world thing,'' Imp commented, ``That's not very long.''



``I'd settle for letting him stew for a few days,'' Defiant said.



He moved the cursor on the screen without moving his hands.  Something in his eyes?  His brain?



He went to a tab beside the highest priority threat.  It was red, and there was a number inside it: 8.



It was updates.  New information that had come up in the last few minutes.  Pictures.



Defiant scrolled through the images of the Simurgh, floating in the air above the ocean in the middle of the day.  The last one was from just an hour ago, showing her in early evening, utterly still.



The last three images weren't of the Simurgh.



Bohu.  The towering Endbringer.  The keeper, the siege tower, the invader.



It was hard to think of the terms that applied to Bohu alone.  Tohu and Bohu were usually referred to as the Twins.



But Tohu was nowhere to be seen.



And Bohu had situated herself in the middle of a field.  The ground was only beginning to reshape beneath her, twisting into structures, walls, a maze of stone, soil and grass, of arches and pillars without anything to support.



She simply loomed, her impossibly long arms hanging at her side, head slightly bowed, her eyes shut.



The other images showed the same thing from different angles.  One from the other side, then another from directly above, showing the alterations to her surroundings as concentric circles.



It was daylight.  Going by the times of the photos, she was on the opposite side of the planet, roughly, from the Simurgh.



``Holy fuck,'' Canary murmured.  ``Two at once?''



``It's another thing on the list of shit we can't do anything about,'' Imp said, her tone cavalier.  ``No sweat, no sweat.''



``Right.  We need to focus on what we can handle.  Next on the list of issues we need to address are the Blasphemies,'' Defiant said.



``No\ldots'' I said, trailing off.  I was thinking of something Dinah had said, when she'd described the way things would go down at the end of the world.



\emph{Five groups}.  Each with capes from around the world, with armies.



Four Endbringers and Scion?  Or something else entirely?



``\ldots{}No.  Let's pay a little more attention to what's happening here.''





