





``You have something in mind?'' Defiant asked.



``No,'' I said.  ``But we're dealing with problems on a massive scale.  We need to look for solutions on that same scale.''



``Um,'' Imp said.  ``You just leaped from the subject of talking about the Endbringers to talking about solutions.''



``Yeah,'' I said.  ``I think we \emph{definitely} need to think about solutions, Endbringer-wise.''



``Oh, well, of course,'' Imp said.  ``This is doable.  Something we've managed once in the last thirty years, taking down Endbringers.''



``Shh,'' Tattletale said.  She turned to me.  ``There's more to this.''



``Dinah told me the defending forces would be divided into five groups.  Armies, individuals, some of the biggest capes, and unknowns.''



``She said that to others.  It's on record in the PRT,'' Defiant told me.



``Five groups in different places, and Dinah couldn't see \emph{why} they were there, she couldn't see the particulars.  She said there could be too many precogs there, but what if that's not it?  What if she's blind about the particulars because the \emph{Endbringers} are there?''



``A coordinated attack?'' Narwhal asked.



I nodded.  ``It's possible.  Either it's Leviathan, Simurgh, Tohu, Bohu and Khonsu, or Scion's there and Tohu and Bohu are together, as usual.''



``I can't imagine the defending forces would hold the line for very long, if at all,'' Defiant said.  ``Not if we're spread that thin.''



``A situation this dire brings out all of the people who might not otherwise fight,'' I said.  ``Parian wasn't a fighter, but when Leviathan hit Brockton Bay, she stepped up to the plate.  As things get worse, we might see some people doing the same.''



``If it's five Endbringers and Scion we're up against, we might see people giving up altogether,'' Narwhal pointed out.



I nodded.  ``Tattletale already said something like that.  Yes.  A lot hinges on whatever comes next, whether we can get people on board.  Whether \emph{others} are doing the same.''



``Alright,'' Defiant said.  ``You have something in mind for the Endbringers?''



``A pre-emptive attack,'' Narwhal said, her voice quiet.  ``If it provokes them to lash out, well, at least it's not a \emph{coordinated} attack, and at least it's at a point in time when Scion's busy elsewhere.  The Simurgh is standing still.  We could hit her with something like what we used in New Delhi or Los Angeles.''



``We could,'' Defiant agreed.



``Let's think on it?'' I suggested.  ``We can't do this without laying out the groundwork, and that means convincing people this \emph{isn't} hopeless, it means gathering information, getting resources together.''



``Then do your thinking as you get ready,'' Defiant said.  ``Gear up.  Gather anyone you think you need.''



``I'm set,'' Tattletale said.  Imp and Rachel nodded.



``I'll need my spare costume pieces from the Dragonfly,'' I said.  ``I parked it in Gimel before I left for the rig.  Hoping my flight pack has enough of a charge.''



``Go,'' Defiant said.  ``I'll see to Saint.''



``And me?'' Canary asked.



``We can get you a standard Protectorate costume.  Spider silk,'' Narwhal said.  ``Durable, flexible.  No frills, nothing fancy, but it'll be better than nothing.''



Canary frowned.



``What?'' Narwhal asked.



``Just\ldots skintight suits.''



``Got a bit of pudge there?'' Imp asked.  ``Fat thighs?  Cankles?''



``I don't have cankles,'' Canary said.  ``Or fat thighs.  But it's not\ldots''



She trailed off.



Imp plucked the fabric of her own costume. ``I've been there.  You think looking this good is \emph{easy}?  Skintight is a bitch to pull off.  Diets, exercise, keeping up with the patrols and the life or death fights.  Surprised you didn't get that while you were in the slammer.''



``Not a lot of choice in food, or freedom of movement when you can get cut in half for setting one toe in the wrong spot,'' Canary said.  She was frowning, now.



``You can wear your clothes over it,'' Narwhal suggested.  ``We can get you some tools.  Nonlethal weapons.  So you're able to defend yourself.''



They'd work it out.  I shook my head a little.  Had to focus on my own thing.



``Doorway, please,'' I murmured.  ``Gimel.  By the Dragonfly, New Brockton Bay.''



The portal began to slide open.



``I'll do you one better, Canary,'' Saint said.  ``I'll give you one of the spare Dragonslayer suits.''



``It's\ldots a good offer, but I think I'd feel like I was betraying Dragon if I took it.''



``You wouldn't be able to pay her what you supposedly owe her if you died, either,'' Saint said.  ``This is freely offered.  No strings attached.  I'll give you the ability to \emph{fly}, Canary.  Better nonlethal weapons than the ones they have Masamune manufacturing.''



``I don't know,'' she said.



I hesitated in the doorway to listen.  Tattletale, Rachel and Imp walked past me on their way through.



``Do it,'' Defiant said, not looking at Canary or Saint.  His eyes were on the laptop.  ``Saint?  I'll be looking over \emph{everything} for tricks and backdoors.''



``Noted,'' Saint said.



Defiant opened the door to Saint's cell.



Saint stood, then rolled his head around, as if getting kinks out of his neck.  He looked so small next to Defiant, but he wasn't a small guy.  His face was marked by lines of stress, but his gaze was hard.



``You don't leave my sight,'' Defiant said.  ``Any access you have to a system is routed through me.  I double-check it.''



Saint nodded.



I passed through the portal, entering the field where I'd set down the Dragonfly. Some kids were climbing around the outside of the ship, but they ran the second they saw us, shouting.



The wind blew, making waves in the tall grass.  I turned to face it so my hair wouldn't blow into my face.  I was left looking out over the water, while I moved bugs into the necessary channels and manipulated the switches, bidding the ramp to open.



``It doesn't get said enough, but this is pretty damn cool,'' Tattletale said.  ``Outclassed convenience-wise by the portals we've got access to, but yeah, \emph{nice}.''



``Yeah,'' I said.  My mind was almost someplace else, considering everything that was in play, the threats, the necessities.



I paused, glancing out at New Brockton Bay.  Brockton Bay Gimel.  Tents and shelters were spread out everywhere, with ramshackle shelters dotting the landscape with little sense or organization.  Here and there, there were paths forming, where the passage of hundreds of people were tramping down grass and disturbing the earth.  Crews of people working in groups to erect basic shelters, bringing down trees and reducing them to basic components that they could form into shelters.



I felt a stirring, a mix of emotions, at seeing that.



Looking at them, I could almost sense that they were blissfully unaware.  They didn't know how badly we'd lost in our initial foray, or their attitudes would be different.  There wasn't anything like television or radio to spread the word.  There would only be word of mouth.



Had someone told them, only for the masses to dismiss it as hearsay?  Dismissing it because they didn't want to \emph{believe} we were well and truly fucked?  Or had the word simply failed to spread, with enough people keeping quiet, believing that it wouldn't do any good for people to know?



They were lucky, to be able to face the end of the world without full knowledge of what we were up against.  Without the knowledge of what Scion was, or the looming, patient presence of the two Endbringers on Earth Bet.



It was arrogant, even condescending, but I felt a kind of warmth in the center of my chest when I looked at the people down there, like a parent might feel for a child, accompanying a sort of pity.



And somehow, when I pictured the people going to work, sweating, dirty, hungry and scared, getting eaten alive by flies, selflessly carrying out barn raisings to give shelter to the old, the infirm and the very young, I couldn't help but picture my dad in their midst.  It was the sort of thing he'd do.



Nobody had explicitly said he'd died, and I'd gone out of my way not to ask.  Still, I felt how wet my eyes were when I blinked.  No tears, but my eyes were wet.



I could envision Charlotte down there.  Sierra.  Forrest.  The kids, Ephraim, Mason, Aiden, Kathy and Mai, I imagined, would be bringing water to the people hard at work.



Except Sierra had other duties, and the orphan children from my territory were older.  The kids would be doing basic jobs by now, overseeing new batches of kids with the errands, sweeping, and other stuff in that vein.  Still, it was a mental picture that defied logic, like seeing my dad down there.  I pictured them with the water bottles.



I shook my head a little to rid myself of the mental image, and in the doing, I stirred myself from the daydreaming entirely.  I was still standing at the foot of the ramp.



``Lost in thought?'' Tattletale asked.



``Sorry,'' I said.  I turned to make my way up the ramp, Tattletale keeping pace beside me.  Rachel had already settled in, lying on a bench, Bastard lying on the ground just below her.  Imp had settled outside in the grass, her head turned towards what would have been the south end of the city, if the city existed in this world.



``No need to apologize.  Constructive thought?  Strategy?''



``No.  Not constructive at all,'' I said.  ``Thinking about the people.''



``The people?'' Tattletale asked.  ``We keep telling them to split up, that we'll give them portals to different spots around Gimel, or to other Earths.  The ones down there are the ones that refuse to go.  Sitting there, clustered into a massive target for Scion, the Endbringers, or the Y\`{a}ngb\v{a}n to take out.''



``Yeah,'' I agreed.  ``Everything I've said in the past stands.  Humans are idiots.  They're selfish and injust and unfair, they're violent and clumsy and petty and shortsighted.  Don't get me wrong.  Every part of that applies to me, too.  I'm not setting myself above them on any level.''



``Mm,'' Tattletale responded.



I began gathering the components for my suit.  I'd wear the same thing I did to the fight against Scion.  Just needed the individual parts.



``But at the end of the day, sometimes humanity isn't so bad.''



``Sometimes,'' she said.  ``Took me a while to realize that.  The more you find out, the uglier things tend to look.  But you keep looking, and it's not all bad at the end.''



I nodded, reaching into my pocket to get the little tube of pepper spray I'd claimed from my ruined costume.  I moved it into the belt of the new costume, then began stripping out of the casual clothes I wore.



I paused when I had my shirt off and my hair more or less in order, holding the bundle against my chest.



``I want to save them,'' I said, surprising myself with the emotion in my voice.



``Scary thing is,'' Tattletale said, ``I know what you mean.  Most times, I'm just not that fond of \emph{people}.  Seen enough ugliness in them that I don't\ldots care?  No.  That's wrong.  I care, I \emph{cared, }past tense.  But I didn't\ldots mind, if something happened to them.  That's closer to the mark.''



I nodded.  I wasn't surprised at that.



``But we're getting to this point where I want to do something for them like I wanted to do something for you.  Probably a bad omen.''



``No,'' I said, quiet, as I strapped on armor.  I looked at her.  ``Do you regret reaching out to me?''



``No,'' she said.  ``But that doesn't mean it was all \emph{right}, know what I mean?''



I nodded.



Tattletale gave me a pat on the back before making her way to the bench opposite Rachel, grabbing a laptop and lying down with her head and shoulders resting against a bulkhead.



Belt on.  I hesitated before donning my mask, but I pulled it on anyways, then clasped it behind the neck, unrolling the bit from the body-portion to bury the clasp.



Then I pulled on the spare flight pack.



Depending on how things went, I might not get the chance to charge it again, to refuel the Dragonfly or anything in that vein.



If Scion or the Endbringers didn't kill us in the coming handful of days, we'd eventually run out of fuel.  Communications would falter, and we'd run through stores of food, medicine and other amenities.  There was no way to establish new supplies as fast as we needed them.



We'd only been able to evacuate with limited supplies.  Then there were the supplies we'd brought over in advance.  Gimel was one of the more fortunate Earths for that.



I checked my armor, then tightened the straps.  Maybe a bit tighter than necessary, but I wasn't going to stress over it.



I opened and closed my hand.  It felt weird, still, but not so much that it would be debilitating.



``Doorway,'' I said.  ``To Panacea.''



The doorway unfolded, and noise poured forth from the other side.  I got Imp's attention with a swirl of butterflies, then drew the other bugs in the area to me.  Once Imp was inside the Dragonfly, I bid the ramp to close.



The rear door of the Dragonfly was still slowly shutting as we passed through the doorway and into the center of what looked like a makeshift hospital.



The walls seemed to be rough granite in varying colors, surprisingly thick and \emph{old}.  Bricks and blocks three feet across, some with cracks here and there.  There were even tendrils of grass or occasional flowers growing in some of the deeper crevices.  The `windows' were openings five feet by ten feet wide, with glass set into frames that had clearly been added as a late addition.



The area was flooded with people, talking, shouting, whimpering, crying.



Patients.



People had been burned, cut, bruised, their limbs crushed, faces shattered.  There were wounds I couldn't imagine were anything but parahuman made.  They were laid out on beds and sat on stone chairs, crammed so close together they were practically shoulder to shoulder.



Panacea appeared.  She was rubbing wet hands as though she'd just washed them.  Long sleeves were rolled up, her hair tied back.  Unlike what Canary had suggested, she was leaner as a result of her stay in the Birdcage.  She was followed by a man with hair that had been combed into a sharp part, a needle-thin mustache and heavy bags under his eyes.  Something in his bearing\ldots he was a cape.



She walked by a row of people, and they extended hands.  Her fingers touched each of theirs for only a moment, while she didn't give them even a glance.



``Dad,'' she said, stopping.



A man at the side of the room stood straighter.  Marquis.  His hair was long enough to drape over his shoulders, his face clean-shaven by contrast.  He had a fancy-looking jacket folded over one arm, and a white dress shirt that had fine lines of black lace at the collar and the sleeves he'd rolled up his arms.  Two ostentatious rings dangled from a fine chain around his neck; the chain had a locket on it, suggesting he'd added the rings as an afterthought.  To keep them out of the way while he worked, perhaps.



``What is it, Amelia?''



For another man, the combination of physical traits and the style of dress might have led to someone mistaking them for a woman.  They might have come across as effeminate.



Marquis didn't.  Not really.  When he'd spoken, his voice had been masculine, deep, confident.  The cut of his shoulders and chin, his narrow hips, was enough that I couldn't expect anyone to mistake him for a woman.  I wasn't the type to go for older guys, I wasn't even the type to go for effeminate guys.  But I could see where women would go for Marquis.



``Broken bones here.  Shattered femur.  Some bone is exposed.  Are you occupied?''



``Nothing critical,'' Marquis said.  ``It won't be comfortable, fixing that.''



Panacea touched the patient's hand again.  ``He'll be pain-free for twenty minutes.''



``That's enough time.  Thank you, my dear.''



Marquis crossed paths with Panacea on his way to the patient.  He laid a hand on her shoulder in passing.



I watched her reach one hand up to her upper arm, touching a tattoo.  She took in a deep breath, exhaled, and then moved on.



She got two paces before she finally noticed us, stopping in her tracks.



``Yo,'' Tattletale said.



``Is there a problem?'' the tidy man beside Panacea asked.



``Old acquaintances,'' Panacea said, her stare hard.



``Enemies?''



``\emph{One} enemy,'' she said, her voice soft.  ``I wasn't exactly looking forward to seeing you again, Tattletale.''



``Sorry,'' Tattletale said.



``I can deal with this, if it's what you require,'' the tidy man said.



``No, Spruce.  You probably couldn't.  Don't worry about it.  Think you could double-check on things in the back?  The equipment?''



``I will,'' the tidy man said.  He turned and strode from the lobby of the makeshift hospital.



Panacea closed the distance.



``\emph{You do the talking},'' Tattletale whispered.  I nodded a fraction by way of response.



``So?'' Panacea asked.  Her eyes roved over us, taking in details.



``I wanted to thank you for the fix,'' I said.  I raised a hand.



``You tried to help me at a bad time.  It didn't take, but you tried,'' she said.



``Ah.''



``A lot of people invested in your survival.  Caught me off guard.  Used to be I was the golden child, but I wasn't lucky enough to have anyone there to catch me when I fell.''



``Looks like Marquis caught you,'' Tattletale said.



Panacea glanced at her dad, who was looking at us with one eyebrow slightly raised.



``Maybe,'' she said.  ``I thought you were a hero now.  You're running with the old gang?''



``\emph{Gang} is such an outmoded word,'' Imp said.  ``So \emph{small}.  There's gotta be a better way to put it.  Ruling the roost with the old \emph{warlords} again, back atop Mount Olympus once more.''



``Shh,'' Tattletale hushed her.  Then, after a pause, she whispered ``\emph{Olympus?  Where are you getting this?}''



``Not a hero, not a villain.  Just trying to get by,'' I said.  ``Sticking with the people I know best.  People I trust.''



``I see.  We're trying to get by, too.  Twelve doctors, twenty nurses, me, my father and what remains of my father's old gang.  They were sending the worst of the wounded our way while we tried to get set up to accommodate larger numbers.  Then the Y\`{a}ngb\v{a}n hit a settlement.  We've been flooded ever since.''



``I see,'' I said.



She shifted her weight.  She had a different presence, now.  Something she'd no doubt picked up in prison.  Not posturing.  Simply more comfortable in her shoes.  She asked, ``Did you need something?  There's a reason you came.''



``I was going to say we're mobilizing.  Dealing with some threats.  Trying to get as many big guns on board as we can, starting with the ones who weren't on the platform.  I was thinking we could use you.''



``I see,'' she said.  ``I'm not particularly interested in being \emph{used}.''



``That's not what I meant.''



``I know, but it's still meaningful that the word came up, isn't it?''



``No,'' I said.  ``No it isn't.''



She glanced back towards her dad.  Two more people who might have been capes had approached him, while he sat next to the man he was healing.



``I can't stop Scion,'' Panacea said.  ``I probably couldn't even touch him, if I wanted to get that close, and if I did, I don't think I'd accomplish a thing.''



``Maybe not,'' I said.



``Do you think you're going to stop him with giant dogs?  With bugs?  People tried and they failed.  \emph{This} is what's left.  Finding places where humans used to live and moving in, if we're lucky.  Starting over from scratch if we aren't.  Ensuring that the population is spread out enough, but not so spread out they won't be able to repopulate.  Dividing all of humanity into groups of six hundred to a thousand people, dropping them off in the middle of nowhere.''



``It won't work,'' Tattletale said.  ``Scion moves too fast, and there's not that many places to hide, in the grand scheme of things.''



``Every time you open your mouth,'' Panacea said.  She sounded as if she was going to say something else, but she didn't.



``You're one of the strongest capes out there,'' I said.  ``We need you on our side.''



``You'll have me,'' Panacea said.  ``But not on the front lines.''



I sighed.



A deep rumble sounded.  An animal noise, almost.



I turned to look, and I saw Spruce, the tidy man, standing beside Lung and Bonesaw.  The noise had been Lung, an odd sound to come from him when he was still, to all appearances, in his human state.  A tall Asian man, muscular, riddled with tattoos.  New ones had been added since the first day I'd seen him.  More eastern-style dragons.  His hair was longer, and there was scruff on his cheeks and chin.



Bonesaw wasn't dressed up like a little girl.  Her hair wasn't in ringlets.  She wore gray sweats.



Rachel growled a little, under her breath, an eerie parallel to Lung.



Lung stepped forward, and he pushed Bonesaw, who stumbled a little.



``It's not nice to push,'' she said.



``Don't be cutesy,'' he growled.  ``We've warned you before.''



``Okay, fine then.  Stop \emph{fucking} pushing me.  Tell me where you want me, and I'll walk there.''



He pointed towards us.



They closed the distance until Bonesaw was next to Panacea.  Lung placed a hand on top of her head and gripped her, arresting her forward momentum.



She lashed out, twisting around and slapping at his wrist with one hand.



``\emph{Don't} do that,'' she said.



``\emph{Someone's} short-tempered,'' Imp observed.  She hadn't yet donned her mask, though she had it with her.  Her eyes were narrowed.



``I've had \emph{no} sleep,'' Bonesaw said.  ``Big sis here took out all the good bits I'd stored inside myself, and she didn't turn off the pain.  I feel too light.  I feel \emph{weird}.  Can't sit still, not that they ever \emph{let} me.''



``First tier parahuman problems,'' Imp said.  Her tone wasn't as humorous in nature as the words.



``And they keep getting on my case,'' Bonesaw said, apparently oblivious.  She directed her attention to Panacea and Lung.  ``Trust me, I haven't butchered you all yet, I'm not going to in the future.  You can stop \emph{testing} me.''



``I remember when you were cuddly,'' Tattletale said.  ``You were so happy and fluffy and you had a good \emph{attitude}.  You were a complete and total monster, and nobody in their right mind would cuddle you, but you were adorable.  Now look at you.''



Bonesaw scowled, but I wasn't paying attention to that.  Tattletale had used the past tense.  \emph{You were a complete monster}.  Referring to the past, or an observation on a deeper level?



``\emph{She} is why I can't leave,'' Panacea said.  ``I'm the only one that can double-check her work.  If we're both here, you've got two stellar healers on the back lines.  If I leave, you've got a healer with minimal combat experience on the front line and a defused bomb with nobody that's capable of knowing if it's reactivated.''



I couldn't really argue that.



Well, I \emph{could}, but not very well.



``There's another way to deal with that sort of situation,'' Imp said.  ``Get rid of the fucking bomb.''



``We will,'' Panacea said.  ``\emph{If} she gives us an excuse.  Any excuse at all.  But she gets one chance.''



``When you're talking about a bomb, that's all it needs,'' Imp said.  ``Then you wind up carved up, your insides decorating the walls of a room.''



``Your metaphors\ldots'' Tattletale mumbled.  ``Well, that almost worked.''



Bonesaw raised an eyebrow.  ``You sound upset, but I don't remember doing that to you.''



``My \emph{brother},'' Imp growled the word.



``Oh,'' Bonesaw said.  She glanced to her left, then down to the floor, a frown crossing her face.  ``Right.  I'm remembering now.  Shit.  That was one of the bad ones.  Not one of the \emph{bad} bad ones, but bad.''



``\emph{Kind of}, yeah,'' Imp said, not easing up in the slightest.



``I'm sorry,'' Bonesaw said, still looking at the floor.  ``I won't say I'll make amends, because there's no way I can even come close.  I don't know what to say, except that I'm sorry.  No excuses.  But I'm going to do what I can to make things better, and maybe I get a hundredth of the way, in the end.''



``He had a second trigger event,'' Tattletale said.  ``And killed Burnscar.  In case that helps you place him.''



``I said I \emph{remember},'' Bonesaw said, sounding irritated.  She glared at Tattletale.



``\emph{Sure},'' Tattletale replied, quiet enough she could barely be heard.



I stared at Bonesaw, watching her expression shift in fractions.  Her eyes moved, as if she were watching a scene, or recalling a memory in great detail.



``You're fighting?'' Lung asked, interrupting my thoughts.



``We're fighting,'' I said, shifting my attention to him.



``Who?''



``Everyone who gets in our way,'' Rachel interjected.



``What she said,'' I added.



Lung stared at me, and I held his gaze.  For someone as brutal and vicious as he was in the heat of battle, Lung had cold eyes.



He'd be thinking about his losses to me.  I'd used venomous bugs to rot away his junkular area, and I'd dosed him with hallucinogenic blood before gouging out his eyes.



It was odd, but those slights probably mattered less than the \emph{real} offense I'd dealt him.



I'd taken over the city.  He'd tried and failed, I'd succeeded.



Given my understanding of Lung, I suspected that was something far more unforgivable.



``Fighting Scion, Endbringers, the \emph{Y\`{a}ngb\v{a}n}\ldots''  Tattletale said.  She placed an emphasis on the last.



Odd.  I would have reversed it.  Emphasized the biggest threats.



``Yes,'' Lung said.  ``No need to manipulate me, Tattletale.  If you want me to join the fight, you only have to ask.''



Tattletale had a funny look on her face, fleeting.  She turned my way, one eyebrow raised, questioning.



I nodded.



``Good,'' Lung said.  ``Let me collect my mask.  I will be back.''



He left.



``Doorway,'' Tattletale said.  ``Um\ldots?''



``To Shadow Stalker,'' I said.



The portal began to open.  It was nighttime on the other side.



Tattletale gave me a funny look.



``What?''



``I brought up the Y\`{a}ngb\v{a}n because I figured he'd be ticked they attacked this spot.  I'm getting credit for brilliant insights I didn't have.  Not even in a fun way.  That's going to bug me.''



I shrugged.  ``Take what we can get?''



She nodded.



While we'd exchanged words, Panacea had sent Bonesaw off with Spruce.



``Thank you again, Panacea,'' I said.  ``For putting me back together.''



She opened her mouth to speak, then seemed to reconsider.  She pointed at the portal.  I nodded, and followed her as we strode through.  Tattletale and Imp remained in the hospital lobby, and the portal remained open.  Rachel followed us through, but seemed to sense that we wanted a private discussion and wandered off a short distance.



Panacea and I walked out onto a shelf of rubble that had once been the midpoint of a bridge.



``I'm not a fighter,'' she said.  ``I hope you understand.''



``I do,'' I said.  ``But I'm kind of hoping that, in the end, we aren't left with only the people who `aren't fighters' on the battlefield, who've realized they have no choice but to change their minds.  It'd be pretty tragic if we got that far and someone like you clued into the fact that you \emph{could} have helped.  It would be somehow fitting, too, if that's how humanity went extinct.''



``It would be just as tragic if we rushed headlong into a fight, and threw away a life in the process, only to realize in retrospect it was someone vital,'' she said.



I nodded.



``Good luck.  Don't turn your back on Lung.''



``I won't.  I'm pretty good when it comes to keeping an eye on people,'' I said.  I called bugs to my hand, as if to illustrate.



``Then I really hope you succeed in the fights that come.  We're kind of counting on you.''



``Likewise,'' I said.  ``I mean, I hope you achieve whatever you're striving to do here.''



She glanced back towards the portal, which glowed from the ambient light of the room on the other side.  ``Second chances.''



``Hm?''



``Together, we're giving second chances to monsters who don't deserve them.''



``Yourself included?'' I asked.



She nodded.



``I'm not sure I get it,'' I told her.  I could see Shadow Stalker land to perch on an outcropping of steel reinforcement, a distance away, watching us.  ``I mean, I \emph{do} get the second chances thing, not deserving it.  But\ldots''



I trailed off.  I couldn't articulate it well enough.



``When you're in that position, sometimes the only people willing to extend those second chances to you are the people who need them.''



``I understand,'' I said.  ``You know, if you'd joined the Undersiders back then, we could have given you that.''



``You could have.  I'm not sure I could have taken it.''



``Right,'' I answered.  ``Yeah.''



``Not all of us are like that, though,'' she said.  ``Lung isn't, as far as I can tell, but maybe you'll see it if you look for it.  Or maybe you'll get burned to a crisp by Lung the second an enemy distracts you and you forget to watch him.''



I nodded.



``He's not someone who builds or rebuilds.  He's someone who destroys.''



Something in that phrase struck a chord in me.  I knew the right answer, right away.



``We just need to point him in the right direction, then,'' I said.



``Best of luck with that,'' Panacea said.



She'd had her hands clasped, and as she extended a hand to shake, I could feel the bugs come to life, fluttering free of the space between her palms.



Relay bugs.  Twenty.



I checked, investigating their internal makeup.  They could \emph{breed}.



Even with that gift, even with the fact that she'd never done anything to me, I couldn't help but think of the incoherent mess of details I'd seen in the records.  The pictures that catalogued the event that had preceded her voluntary admission to the Birdcage.  I saw her outstretched hand and hesitated for a fraction of a second.  From the expression on her face, I knew she had noticed.



\emph{Second chances}.



I shook her hand, drawing the relay bugs to me and stashing them in my belt.  ``Thank you.''



She nodded, then exited the portal as the others made their way through to my side.  Lung and the Undersiders.  I had my back turned to them as I looked at Shadow Stalker.  She remained perched on that twist of bent girders and bars from the collapsed bridge, her cloak flapping around her.



``I remember this one,'' Lung rumbled.  ``She shot me with arrows.  It did not hurt that much.  She is a weakling.  Why are we wasting our time with her?''



\emph{And so the struggles for dominance in the group begin}.



``I'll take weak,'' I said.  ``I'm just\ldots working with known quantities.''



The flapping of the cloak quieted as she shifted into a shadow state.  The wind was passing through it, instead of pushing against it.



Shadow Stalker leaped down, floated.



Soundlessly, she landed right in front of me, remaining in the shadow state.



``Hoping you've changed your mind,'' I said.  \emph{Hoping you've seen the devastation, and that it's reached some human part of you that cares}.  ``That you're interested in fighting.''



She didn't budge, didn't respond.



``It also means bashing some skulls,'' I said.  ``She been behaving, Tattletale?''



``Mostly.''



``Then she's probably itching for a good fight,'' I said, not breaking eye contact with Shadow Stalker.  ``What do you say?  You want to knock a few heads?  Break some jaws?''



She shifted to her physical state.  ``I'm not that easy to bait.''



I shrugged, waiting.



``Search and rescue is garbage,'' she said, sounding annoyed.  ``Nobody left, but there's no place to go if I \emph{don't} want to do it, either.''



``You could go home,'' I said.  ``Find your family, settle down, put the crossbow away for good.''



``Capes don't retire,'' Shadow Stalker said.  ``Doesn't work.  We die in battle or we lose our minds, one or the other.''



I thought of my passenger, how it had reflexively sought out violence in the past.  How others had done the same.  \emph{Die in battle}.



Then I thought of Grue.  Was Shadow Stalker right?  Would the retirement just fail to take?



I sighed.  ``So?  What's your call?''



``I'll come.  Sure.  I kind of want to see what you've made of yourself.''



She had wanted to claim the credit for my becoming what I'd become.  It grated, because it wasn't entirely wrong.  It wasn't true in the sense she believed it was true, but she \emph{had} given me my powers.



``Fine,'' I said.



She cracked her knuckles.  ``So, who's first?''



``Need to talk that over with Defiant,'' I said.  ``We can do it over the comms, for the sake of expediency.''



``Okay,'' she said.  She sounded a little pleased with herself.  ``Whatever.  I'm game.''



``Doorway, please,'' I said, to nobody in particular.  ``Dragonfly interior.''



The portal opened.



I extended a hand, inviting the group to enter.



Lung shouldered his way past Rachel to be the first one inside.  Bastard huffed out a half-bark, then growled.



Much like Panacea had said about Bonesaw, it wasn't about having them as allies.  Having them be part of the group, it meant they weren't on the opposing side.  They weren't wreaking havoc as neutral parties.



That alone was good.



But if they turned out to be destructive forces we could \emph{control}\ldots



The half-thought I'd had during my goodbye to Panacea fell into place.



A plan.



I stepped through the portal to board the Dragonfly.



\blacksquare



``You \emph{lunatic}!''  Shadow growled the word.



I was silent.  The clouds above and landscape below were a blur, the individual details impossible to make out with our speed.



``Doing this with \emph{me}?  With \emph{Lung}?  I could almost understand that,'' Shadow Stalker growled.  ``But your friends?''



``Don't care,'' Tattletale said.  ``We've always been the sort to go for the long odds.  You have to do what your enemy won't predict.''



``Damn straight,'' Imp said.  ``Credo I live by.''



``Mount Olympus, now \emph{credo}?''  Tattletale asked.  ``It's the Heartbroken, isn't it?  They're warping you into\ldots this.''



``Leave me alone, seriously.''



``What you're saying doesn't make \emph{sense}!''  Shadow Stalker snarled.  ``Not here, not like \emph{this!}``



``It actually makes the \emph{most} sense,'' Tattletale said.  ``But that's a different story altogether.  One that needs some explanation.''



``Ten minutes before we hit our target,'' I said.  We'd taken the path through the Brockton Bay portal.  Cauldron's doorways weren't big enough for a vehicle like this.



``Ten minutes should be enough,'' Tattletale said.  ``Let me get this loaded on the laptop.  Easier to show than tell.''



``Right,'' I said.  My eyes didn't leave the navigation screens.



``I'll \emph{kill} you,'' Shadow Stalker threatened.  ``Turn this fucking ship \emph{around}.''



She moved, reaching for a crossbow bolt.  I reacted, half-rising from my seat, drawing my swarm out-



But Lung moved faster, shoving Shadow Stalker against the side of the ship.



Shadow Stalker went ghostly, brandishing the bolt like a dagger as she passed through Lung.



Rachel gripped a length of wire that extended from the laptop, holding it out like a garrotte.  As Lung had done, she moved to pin Shadow Stalker against the wall of the Dragonfly.  Shadow Stalker returned to a normal state just in time to avoid being electrocuted.



Bastard growled, snapping at her hand, and the bolt clattered to the floor.



``You're \emph{okay} with this?''  she asked.



``Yes,'' Lung rumbled, by way of response.  ``This might be best.''



``Fuck you, Hebert!  Pulling this shit only after you got me on board?  You're all \emph{lunatics}!''



I sighed.



Tattletale sat down on the arm of my pilot's seat, setting one foot down beside my thigh on the seat's edge.  ``There's stuff you need to know.  I told you before, you said you wanted to be blissfully ignorant until the last minute.''



``Yeah,'' I said.  ``Yes.  Right.  I'm listening.''



``It's video footage Glaistig Uaine left with me.  Last two minutes of Eidolon's life.  Video cuts in and out, but there's audio.  That leaves me maybe a minute or two to explain, then you can use the rest of the time to think it over.''



She had my attention, though I couldn't take my eyes off the monitors at the front of the ship.  Shadow Stalker's cries of anger were background noise.



The \emph{Pendragon} was flying alongside us, just a little behind, carrying the capes Defiant had recruited.  Carrying Saint, Canary, and others.



Tattletale loaded up the video, filling the screen of the laptop.



I glanced once at the main monitor, then set the autopilot.



Faultline had talked about taking the simple route.  Talking to Scion.  In practice, harder than it seemed.



We were dealing with problems on a massive scale, we needed solutions on that same level.  There was no easy way to get to that level.  It meant taking risks.  Gambling.



We needed a destructive force we could \emph{direct}.  Needed to turn third-party liabilities into assets.



With that in mind, I'd set course straight for the Simurgh.  We'd talk to her or we'd kill her.



Tattletale started the video, and I watched.





