





``We're here,'' I said.



It was enough.  All the different personalities in the Dragonfly, the\ldots how had Tattletale put it, once upon a time?  The people who weren't inclined to play `cops and robbers', who weren't the types to follow the rules or codes, and were \emph{dangerous} without a firm hand.  Rachel, Lung, Sophia\ldots they fell silent.  The fighting stopped.



Because they, even with their unique and personal issues, acknowledged that this wasn't a situation where you fucked around.



Monitors switched settings without any cue from me.  Showing the Simurgh from a distance away, from a different angle.  Defiant had switched on his long-ranged cameras.



A moment later, he switched on the cameras in the Dragonfly.  The two sets of images alternated across the innumerable displays in the craft.  Only the display directly in front of me in the cockpit remained untouched, showing altitude, heading, speed, distance from target, and alerts regarding Scion's latest appearances.



The Dragonfly changed course, angling to maintain a set distance from the Endbringer.  Again, not me.



Defiant seemed content to handle the mechanical end of things.  I stood from my seat, stretching a little, before gathering my bugs.  Two relay bugs, for safety's sake.  They exited the craft.



No scream from the Simurgh.  At least, not one I could detect.  It would fit her to keep it beyond our notice, influencing us, the sort of card she would keep up her sleeve.  To make the psychic scream `audible', for lack of a better word, purely for spreading fear, then use it subtly at a time when she wasn't attacking.



The others in the ship hadn't only gone silent.  They'd gone \emph{still}.  I might have taken it for an almost hypnotic paralysis, a sign that something was deeply wrong, but Rachel turned and found a seat on the bench opposite Shadow Stalker.



No, they were still themselves.



My bugs made their way towards the Simurgh, while I chained the two relay bugs together to extend my range.



Fragile, as it only required the death of one bug to sever my connection with the swarm.  I didn't mind.  If she acted on my swarm, that was likely to be the least of our worries.



Cameras changed focus, zooming in on the Simurgh's face, hands and various wingtips, different cameras taking over as the Pendragon and the Dragonfly rotated around her and the cameras lost sight of the features in question.  Mosaic views of her features, broken up like I might see if I were looking through the eyes of my bugs, but without my power to coodinate the picture, draw it into something cohesive.



In the corner of each image, metrics, numbers, measurements, as if Defiant hoped to track the slightest movement.



It was the hair that got me.  Gossamer-fine, silver-white, straight, it blew in the wind as if each strand were a separate entity.  Not in clumps or locks, but a curtain of strands ten times as dramatic as something one might see in a digitally altered hair commercial.



Artificial.



``Seventy,'' Tattletale said.



``Hm?'' I asked.



``I said I was sixty-five percent sure before.  I'm revising it to seventy.''



I nodded.



\emph{Hello}, \emph{Simurgh}, I thought.  \emph{We finally meet}.



The Protectorate was strict about who could join the fights against the Simurgh.  Capes needed psychological evaluations, they needed to sign documents agreeing to the quarantine procedures, and they needed to be on board with the timetables.



I'd been unable to participate when the Simurgh had attacked flight BA178.  When she'd attacked Manchester, I'd been barred from joining the fight by bureaucratic red tape.  I had a bad history and I was still on probation.  Too likely that I was mentally unstable.



When the Simurgh had hit \emph{Paris}, I'd gone to Mrs. Yamada, hoping for a therapist's bill of clean mental health.  Or, if not quite that, then at least a go-ahead.



She'd advised me to see it as a good thing, instead.  That my participation would be another black mark on my record, another reason for people to be suspicious of me or second guess my decisions.



She'd also very elegantly avoided spelling out that she wasn't willing to give me that clean bill of mental health.  I'd noticed, but hadn't pressed her on it.  She would have been forced to say it straight, and I would have had to hear her say it.



``Ready?'' I asked.



``I do the talking, you pass it on,'' Tattletale said.



I nodded.



Tattletale sighed.  ``Look at her.  The folly of man, am I right?''



``I don't know.  \emph{You} have a better idea about whether you're right, but it\ldots doesn't fit to me.''



``I'm sure.''



``You're seventy percent sure.''



``Seventy percent, yes.  If I'm \emph{wrong}, then I'll be approaching this entire conversation from the wrong angle, and we might wind up siccing an otherwise passive Endbringer on humanity.''



``Let's hope you're right, then,'' I said.



She nodded.



``Everyone ready?'' I asked.  I looked around the craft.  No responses.  Only silent nods.



One head that was shaking.  Shadow Stalker.



I touched the screen on the console.  ``Defiant?''



``\emph{Ready when you are,}'' he said.



``We're starting right now,'' I said.  I nodded at Tattletale.



She rolled her shoulders, took in a deep breath, then sighed.  ``Hello, Endbringer, this--''



I echoed her words, speaking through my bugs as an interpreter might speak in another language.



The instant I had the first word out, alarms went off throughout the ship.  The Dragonfly shuddered as meager weapons unfolded from the sides.  My visual of the Pendragon showed it was reacting much the same way.



Simurgh had reacted.



She hadn't \emph{attacked}, but she had reacted.



She rotated in the air, holding her position, wings flat at her sides.  The wings were purely ornamental, much as Behemoth's bulk and musculature had been.  She used telekinesis to move, and she used it now to keep herself oriented in the air, rotating so she matched our orbit around her, her eyes and attention fully fixed on the Dragonfly.



``Oh, \emph{shit},'' Imp spoke, her voice wavering breathlessly halfway through the `shit'.



Long seconds passed, but the Simurgh didn't take any other action.



``Th- this is Tattletale speaking, one face in that vast, crazy crowd of humans you've been murdering,'' Tattletale finished.  ``Good to see you're listening.  I thought it was about time we had a chat.''



No response, no movement.  Odd, to see the screens showing her depicting the zoomed-in images of her face, hands, wings and body and not see them rotating in the picture as they had been before.



Her expression was neutral, but then again, the Simurgh's expression was always neutral.  A face like a doll's, a cold stare.  Beautiful in every conventional sense, in that every classically attractive feature was there, from the delicate, thin frame to the high cheekbones to the luxurious hair\ldots horrifying in the manner it was all \emph{framed}.  The height that put her two to three times the height of an ordinary adult, the wings that filled the space around her.  The feathers were surprisingly tough and dense, the edges capable of scoring steel.



Not that she really fought in close quarters, where she could help it.



``Let's face the facts, Simurgh.  Ziz.  Israfel.  Ulama.  Whatever you want to go by.  You started acting funny pretty much right away, after Eidolon bit it.  Maybe that's mourning.  Maybe you respected him as an enemy, 'cause he was one of only two individuals who could really give you guys a run for your money.  Or maybe you had a different relationship.''



Tattletale let the words hang in the air.



``Maybe a parent-child relationship?  Maybe he created you.''



The Simurgh didn't move a muscle.  Her hair blew in the wind, and it caught on the features of her face, not even eliciting a blink of her eyes.



I leaned over my chair to hit the button on my cockpit, giving me a view of the inside of the Pendragon.



Defiant, Narwhal, Miss Militia, Saint, Canary, Parian, Foil, Golem, Vista and Kid Win were all present within.  Defiant had collected the heroes, the capes who might have been less inclined to throw their hat into the ring if I showed up in the company of Tattletale, Imp and Rachel.  He'd been closer to Parian and Foil when I approached him with the plan.



I watched the expressions on their faces, the concern, the alarm and confusion I'd felt only minutes ago.  I knew Tattletale hadn't shared this particular detail.  They had to be listening in with some microphone, either a directional one aimed at my swarm outside or one in the Dragonfly.



``They say loneliness breeds the best masters, and it's awfully lonely at the top,'' Tattletale said.  ``Nobody that can really put up a fight, no excuse to flex his abilities to their fullest, nothing that can really give the man any real \emph{stature}, next to Legend, who had all the face time with the media.  No real role to play, compared to Alexandria, who was managing the PRT.  Odd man out.''



I thought of Eidolon, the first time I'd seen him in person.  Meeting in preparation for the Leviathan fight in Brockton Bay\ldots Eidolon had been standing off to one side, in a corner, lost in thought.



``Symbiotic, odd as it sounds, what with you trying to kill him and him trying to kill you.''



Still no reaction.  No response.



I noted the surroundings.  The Simurgh had situated herself above the ocean, an eerie parallel to how Scion had first appeared before humanity.  As battlegrounds went, it left her relatively little to manipulate when using her telekinesis, but it also gave us very little ground to stand on if a fight erupted.  She'd torn apart Flight BA178.  She could tear apart the Dragonfly or the Pendragon if she had a mind to.



Hopefully the other ship would be able to flee, if we couldn't manage an outright \emph{fight}.



Tattletale held up a hand, then spoke.  ``She's not giving me anything.''



I didn't repeat it for the Simurgh.  I only stared at the screens.



``Did you \emph{expect} her to?''  Imp asked.



``Yeah.  Kind of,'' Tattletale said.



``She's not human,'' I said.  ``And, if you're right about this, she's only a projection.  Her brain doesn't work like ours does, if it's even \emph{active}.''



``She responded when we communicated,'' Tattletale said.



I nodded.  ``Defiant, you listening in?''



On the screen in front of us, Defiant turned to the camera, then nodded once.



``Open to suggestions,'' I said.



``We could use powers to try and communicate,'' Narwhal said.  ``Can we express a signal through some other channel?  Through our powers?''



``It might be taken as an attack,'' I said.



``She's smart enough to figure out convoluted chains of cause and effect, but not to take a gesture of communication for what it is?''  Tattletale asked.  ``I say we try it.''



``Oh my god,'' Shadow Stalker said, her voice quiet.  ``You're going to get us all killed.''



``Well, it might be a mercy,'' Imp said.  ``Going out like that, not having to watch the golden man take humanity down piece by piece.''



``Could we try Canary?'' I suggested.  ``If she has any understanding of powers, or if Canary has any influence with things other than humans\ldots''



``\emph{I don't},'' Canary said, from within the Pendragon.  ``\emph{I tried using my power on dogs, cats, birds, monkeys\ldots}''



Tattletale nodded, like this was something expected.  ``Bonesaw said something like that.  When we get our powers, the passenger manages this sort of scan, trying to figure out a way to apply a part of itself.  So Taylor gets a power that's restricted to bugs, Canary gets a power that's limited to people.  At the same time, the passenger kind of figures out if there's any danger of the power harming us, physically or mentally, and it sets down safeguards and limits.  Headaches like Dinah or I get are part of that.  And Eidolon\ldots''



``I don't\ldots I can't believe all this,'' a woman said.  Miss Militia.



``He's really their creator?''  Defiant asked.  ``Eidolon?''



``\ldots{}Sixty percent sure.  Eidolon's some kind of exception, on a lot of levels.  His power works by different vectors, the innate limits aren't there\ldots something \emph{broke, }and I'm betting the Endbringers are tied to it.  Like, this entity is fissioning off into countless fragments that impregnate hosts and somehow a little extra gets tacked on.  Or Cauldron's method of replicating the fragments gets that little extra.''



``Yes,'' Defiant said.  ``But how does that help us here?''



``Getting to that.  Sort of.  Every power has secondary uses, uses that are locked away.  But maybe there's something we can express using the powers, like a kind of parahuman charades.  Not, you know, actually miming something, but giving off a vibe.''



``I'll try whatever,'' I said.  ``Who?  How?''



Tattletale smiled.  ``Oh, this is fun.  It's like a puzzle, but it's not one with a clear cut answer.  Rachel, Canary.  Um.  Imp too.  And Taylor's right.  Any use of power in a way that could be seen as violent might give the wrong cue.  So\ldots none of that.  Let's move people between ships.  Bitch, to the Pendragon.  Leave Bastard behind.  Canary, can you get out on top of your ship?  And Imp, same for you.  We need to distance you from the rest of us.''



``\emph{Outside}?'' Imp asked.



``Outside and \emph{away}.  Where your power doesn't necessarily have a target.  You get me?''



``Three people using their powers,'' Defiant said, ``Without any valid targets?''



``\emph{Exactly},'' Tattletale said.



``I could lose my bugs,'' I said.  ``But I'm not sure I can express my power in a case like that.''



``Even if you could, but that would be pretty heavy handed.  It's what we try next if this fails.  For now, let's work with the existing plan.''



I pulled off my flight pack, then handed it to Imp.



``Oh, fun,'' she said.  ``\emph{God damn it}.''



``No quips?  No jokes?''  I asked.  I helped her find the buckles and straps.



``When I'm done, maybe,'' Imp said.  She glanced at Tattletale.  ``I can't turn my power \emph{on}.  It's always on.  I can turn it \emph{off}, but that only works so long as I'm paying attention.''



``Don't pay attention then.  Leave it running.  We're trying to express an attitude.''



Imp nodded.



``What attitude is Imp?'' I asked.



``Nonviolence, passivity,'' Tattletale said.  ``At least as far as \emph{we're} concerned.''



``And Rachel?''



``A call to arms, expression of strength.''



``And Canary is\ldots cooperation?''



``Something along those lines.''



I nodded.



Tattletale shrugged.  ``Lung would be too violent, and the focus of Vista's power is too\ldots location-driven?  I have no idea how she'd take Narwhal's power, because it's pretty evenly split between offense and defense.''



``Kind of abstract,'' I said.



``I'm\ldots reaching,'' Tattletale confessed.  ``Definitely reaching.  But reaching and abstract thought bought us the portal to Gimel, and I've got to flex my power \emph{somehow}.''



``Somehow,'' I agreed.  ``No, it's worth a try.  Or it will be if it doesn't provoke her to violently murder us all.  Can I make a suggestion, though?''



``Any suggestions are good,'' Tattletale said.



``Send Shadow Stalker instead of Imp.''



``You \emph{bitch},'' Shadow Stalker said.  ``No.''



``\emph{Awesome }idea,'' Imp said.



``Shadow Stalker's power doesn't express itself over an area or any particular medium,'' Tattletale said.  ``It's more personal.''



``Can't she represent \emph{us}?''  I asked.  ``Or can't the personal effect represent us?  If we had Imp flying up there way out of range of any of us, we're still expecting her to represent our group, or humanity as a whole, aren't we?''



``Sort of,'' Tattletale said.



``Then I'm not sure I see the difference,'' I said.



``It doesn't matter,'' Shadow Stalker said.  ``This is \emph{moronic}.  Charades and acting like powers are some kind of massive signal flag for the Endbringer?  You're \emph{lunatics}.''



``Send them both?'' I suggested.



``Oh, that's less fun,'' Imp said.  ``You had a working plan, and you're letting Tattletale convince you otherwise.  Come on.  Send the psycho crossbow girl and I'll hang back here.  My power would send the \emph{total} wrong message.  Totally.''



``Shh,'' Tattletale said.  She frowned.  ``Why Shadow Stalker?''



``Because Imp\ldots is too passive.''



``\emph{Way} too passive,'' Imp murmured.



``So's Shadow Stalker,'' Tattletale said.



``But Shadow Stalker's passenger isn't.  If there are any undertones, any way that the passengers influence our actions, then Shadow Stalker was definitely influenced.  I dug through her old records, read up on her history.''



``What?'' Shadow Stalker asked.



``She got aggressive after she got her powers.  Generally more\ldots'' I searched for the way to phrase it.



``You fucking looked at my records?''



``\ldots{}More violent than most people would be, in her shoes.  Lashing out, aimlessly at first, and then with a target, channeling the aggression.  Except it was the same amount of violence, just concentrated into fewer incidents, alongside a pretty extensive bullying campaign.''



``You're doing this because of a \emph{grudge}?''



``Let's do it,'' Tattletale said.  ``Go with our guts.  Imp and Shadow Stalker, up on the roof.  Bitch, either you or Bastard need to head over to the Pendragon.  Canary on the roof of the Pendragon, singing with nobody listening.''



``You're not getting me outside or any of that shit,'' Shadow Stalker said.



``You're \emph{scared},'' Imp said.  ``That's so cute!  Is it a fear of heights or a fear of the Simurgh?''



``I'm \emph{not} scared,'' Shadow Stalker replied.  ``I'm being \emph{sensible}.  This is lunacy, and for what?  Charades with the Endbringer?''



``That was a metaphor,'' Tattletale said.



``It sounds fucking \emph{stupid}.''



``I've changed my mind,'' Imp said.  ``I'm going.  I'm not going to get lumped in with Sissy McNancypants over here and get called a coward.''



``I'm \emph{not} scared,'' Shadow Stalker said.



``We never really got to meet,'' Imp said.  ``Fight or any of that.  So I've only got the stories I've heard about you.  Like when you shot Grue with your crossbow and it went right through his stomach?  Took him a month to recover?  I used to think, you know, you were a badass.  But you're a pussycat.''



``She's a bully,'' I said.  ``At the end of the day, she only wants to fight opponents she knows she can beat.''



``I've fought two Endbringers,'' Shadow Stalker said, stabbing a finger in my direction.  ``I \emph{know }what you're trying to do.  Fucking manipulating me, getting me into a dangerous situation where you'll get me killed.  Fuck you.''



``Fought two Endbringers as part of an army.  But going up alone, putting yourself in the line of fire against something that much bigger and stronger than you?  No.  You're a bully at heart, and that's the \emph{antithesis} of your usual M.O.''



``Fuck you, Hebert.  Fuck you.''



The sentence left her mouth, and then she stalked to my right, making her way to the cockpit.  She passed through the glass, making her way onto the nose of the ship, where she crouched.  Her flapping cloak obstructed the view, even as translucent as it was, but there was no chance we'd hit anything.



It took a minute to arrange.  Narwhal created a force field platform and carefully moved Rachel over to the Pendragon.  I watched their glacially slow movement and the utterly still Simurgh.



More alarms went off as she moved her head a fraction to watch the floating platform.



It took a few long seconds for my heart to stop trying to jump out of my chest.  Not \emph{completely} oblivious to us petty humans.



``The girl is right.  This seems\ldots ridiculous,'' Lung rumbled.



\emph{Oh, Lung and Shadow Stalker are of like mind, that's wonderful}.



``It is, just a little,'' Tattletale said.  ``But I'm hoping that if this doesn't exactly work, she'll give us credit for trying.''



``The Endbringers do not give you credit,'' Lung said.



``No, guess not,'' Tattletale said.  She bent down to scratch Bastard around the ears, then stopped short when he pulled back, clearly uncomfortable with the stranger.



``Ridiculous,'' Lung repeated himself.  ``And you stopped in the middle of a conversation.  She is waiting for you to continue.''



``She doesn't care.  Ninety-nine percent sure.  Gotta understand, she's not even close to human, especially once you scratch the surface.  We think in black and white, she thinks in\ldots void and substance.  In abstracts or in causative contexts, looking into the future and seeing how things unfold.  So we're going to try this, and maybe something sticks.''



``Mm,'' Lung said, clearly unimpressed.



``Start us up again?''  Tattletale asked me.



I nodded.



``So, Simmy, Eidolon made you, or he's been enough of an opponent that you've kind of got that weird \emph{frenemy} thing going on.  Not in the shitty high school way, but a \emph{real} love-hate relationship.  You know what I mean.  You fight them so long you get to know them, you almost respect them on a level, and that respect becomes something more.''



``You're rambling,'' I murmured.



Tattletale shook her head a little.  ``\emph{Whatever the case}, you're reacting to his being gone.  We're here because we're asking you\ldots''



Tattletale trailed off.  She'd noticed something.



My head turned.  Canary was singing, and I could hear it through my bugs.



Wordless, insistent, filled with a lot of repressed emotion.



Almost \emph{angry}.



I shut it out as best as I could, took a second to focus wholly on keeping my power from communicating any sound to me.  I hit a button on the dashboard, then spent a few seconds tracking down one of Dragon's programs.



Defiant found it first, loading it onto the Dragonfly's system.  It began filtering out the singing.  Most of it.



But no sooner had Canary's Song gone away than the Simurgh began screaming.



Not as intense as I'd heard it described.  Barely audible.



More ominous than anything.



``\emph{Not full strength},'' Miss Militia's voice came over the comms.  ``I give us five minutes.  Wrap this up.''



I unclenched my hands, belatedly realizing I'd been squeezing them so hard they almost \emph{hurt}.  My fingernails throbbed where they'd been almost bent against my palms.  If I'd not been wearing my gloves, I might have pierced the skin.  I flexed my hands to work out the tension that had accumulated and exhaled slowly.



``We're here,'' Tattletale started again, ``Because we're asking you for help.  For vengeance.  For your strength.  We want you and the rest of the Endbringers on board to stop Scion.''



The Simurgh didn't react.



``I don't care if you're doing it to fuck with us, though I'd prefer it if you saved any backstabbing for when Scion's dead and gone.  Fucking wipe us out.  I don't care.  Just so long as we go out with a bang, taking him out with us.''



I made a hand gesture, urging Tattletale to move on.



``\ldots{}Do it for the psychological impact, leave a mark.  Or do it because Scion killed Behemoth, your brother, and some part of you is programmed with a sense of kinship or whatever.  But above all else, I'm hoping you'll help us murder that golden alien motherfucker because he killed Eidolon, and he stripped you of your \emph{purpose}.''



\emph{Sixty percent sure}, I thought.  Tattletale had revised her number.  How confident was she now?



The speech had no meat to it if Eidolon hadn't made the Endbringers.



Very little if he \emph{had}.



Tattletale held up her hand to me again, another sign that I shouldn't repeat what she was saying, because she was talking to \emph{us}.  ``\emph{Fuck this}.  It's like talking to a fucking answering machine.  I feel like some dim asshole with no idea what I'm talking about.  There's no feedback, no responses to read and judge for the next line.''



``Well,'' I said.  ``She's not exactly your usual target.''



``\emph{What do you usually do?}''  Narwhal asked.



``Needle someone until they get upset, then find cues in that.  I'd do that here, except irritating the Simurgh seems like an excuse to get a Darwin Award.''



``\emph{Tattletale's being cautious.  Must be the end of the world after all,}'' someone said.  Might have been Foil.



``She's singing,'' Tattletale said.  ``So that's either a good sign or a very bad sign.''



``\emph{Going by the numbers},'' Miss Militia said, ``\emph{If we assume it's half strength, I'd say three minutes before we have to abort.}''



``Maybe tell Canary to stop,'' I said.



``No,'' Tattletale said.  ``We're getting a response.  Let's hold out.''



``\emph{Then keep talking},'' Defiant said.



Tattletale sighed.  She perched herself on the bench, hands on her head.  ``I don't know if I should continue buying into this Eidolon thing.  Less convinced the further we go.  Most times, you get that key piece of information, and you can coast from there.''



``It's very possible we don't have enough information,'' I said.



``I'm trying to communicate with something that doesn't communicate \emph{back},'' Tattletale said.



``\emph{Reduce},'' Defiant said.  ``\emph{We're trying to convey a message to a being that we don't wholly understand.  You're appealing to sympathy, to revenge.  Something simpler?}''



``Like?'' Tattletale asked.



``\emph{They have a sense of self preservation},'' Narwhal said.  ``\emph{They run when we hurt them enough.  Fear?}''



``Because it allows them to maintain their mission,'' Tattletale said.  ``I don't think we can actually scare her, either.  \emph{Scion} might, but we can't.''



The screaming was getting worse.  Warbling, with highs and lows.  It snagged on my attention, making it harder to maintain a train of thought.



Maybe she was reaching out to us, communicating.  Maybe she was just doing her thing, trying to worm her way into our heads so she could figure out how we functioned, put her plans into motion.



``\emph{Anger},'' Rachel said.



I turned my head.



There was a long pause.  I glanced at the screen on the cockpit to see what she was doing, but she'd stopped by the time I got there to look.  ``\emph{When I cut Behemoth's leg off, after we'd melted most of him away, he was angry.  Stomped around, attacked more.  Kept fighting until he died.  Didn't he?}''



``He did,'' Tattletale said.  ``But now we're getting back to the whole `needling them' issue of the debate.  I'm \emph{pretty} sure I don't want to provoke her.''



``Dunno,'' Rachel said.  ``Just saying.''



``No,'' I said, ``It's good thinking.  It's a possibility.''



I could think back to the images of the Simurgh going all-out.



I remembered the various incidents that had unfolded in her wake.  Echidna, the sundering of the PRT.  Things with ramifications that were affecting us even now.



``\ldots{}A very scary possibility,'' I amended.



Lung gave me a funny look.



``Yes,'' he said, agreeing with me.



Tattletale made a gesture, pointing at herself.



``Go ahead,'' I said.



``Okay, Ziz.  I'm going to be honest.  You're pretty fucked.  You and I both know you were made by somebody or something.  Accidentally, probably.  You were designed to give us as hard a time as possible without exterminating us altogether, probably to feed someone's ego, unbeknownst to them.  But what happens when we're all gone?  What's the fucking \emph{point }of you?''



Tattletale paused.  Waiting, watching.



No reaction from Tattletale.



``What happens when we're all gone?  You're tapped into a power source.  Maybe \emph{most} power sources.  You're draining them dry just to keep yourselves going.  There's nothing for you to do but \emph{linger}, when there's no humans left.  To hibernate.  So you're gathering your forces.  You're planning one last act, probably for a few days from now, where you wipe out humanity, and I'm betting it's one last desperate, \emph{sad} attempt to validate your existence.''



Alarms went off once more.  The Simurgh had moved, her head turning to look over one shoulder, flexing wings to move them out of the way, as if she couldn't see through them but she could see well past the horizon.



She returned to the same posture as before.



``What was that about?'' I asked.



``\emph{Checking},'' Defiant said.  ``\emph{Keep going.  Any reaction is a good reaction}.''



Maybe it was Scion, arriving just in time to pick a fight with the Simurgh.



I could hope.



Tattletale continued, and I repeated what she was saying verbatim, trying to even match her in tone and pitch.  ``Here's what I'm thinking.  Shot in the dark.  You're wanting to fight humanity because you're trying to carry out the old programming, and Scion invalidated that by killing Eidolon, by killing someone else or destroying something.  I think that fighting and nearly killing a few billion humans is the equivalent of fighting and nearly killing Eidolon.  Or \emph{whoever}.''



``One hundred and eighty\emph{ integers of longitude to the west,}'' Defiant said.  ``\emph{Leviathan just arrived.  That's what got her attention.}\emph{We expected one to appear there, so Chevalier ordered us to put crews there with cameras for monitoring.  They're there right now, reporting to me}.''



A monitor shifted, depicting Leviathan, standing on the water's surface in the midst of a heavy rainstorm.  The water around him was rippling, though he was utterly still.



Tattletale continued without pause, not responding or reacting to this information.  ``All I'm saying, all I'm \emph{proposing}, is that Scion's a better bet than we are.  You want to give someone a fucking hard time?  Make that someone \emph{Scion}.  You want to terrorize people?  Terrorize Scion.  Bigger challenge, and you'll probably have the rest of us fucking scared out of our minds if you pull it off.  You want to fucking end the world?  Get in line, chickadee, because Scion's going to beat you to the punch if you don't stop him.''



Tattletale was almost breathless, speaking faster, with more emotion.  It was a challenge to convey that with a voice generated by the swarm.



``Or maybe you don't care.  Maybe you're nothing more than what you appear to be on the surface.  Head games and taking credit for shit you didn't do.  Maybe you're just a \emph{projection}, blank between the ears, mindless, heartless, \emph{pointless}.''



The ship moved a fraction, then adjusted, the autopilot kicking in.



``Did you feel that?''  I asked.  Tattletale had gone silent, and there were no words left for me to translate.



``\emph{We did.}''



A reaction?  I adjusted the monitors, turning everything back to the Simurgh, looking for any clue, any hint.



But she didn't \emph{have} body language.  Every action was deliberate.  She didn't have any that \emph{weren't}.



Tattletale's voice was low.  I did what I could to match it, speaking through a swarm of over a million individual insects and arachnids.  ``You're supposedly this magnificent \emph{genius, }and this is how you go out?  With a whimper?  Petering out like a stream without a source?  You're honestly telling me there isn't anything more to you?''



Another rumble, another shift, somewhat more violent.



``\emph{Enough, Tattletale}.''  Defiant's voice.



``They run on different patterns.  Fair bit of anger, room for some vengeance.  Cleverness, sure.  More in her than in Behemoth.  Some killer instinct, maybe\ldots a blend of fear and caution.  Not so they're \emph{afraid, }but so they can temper their actions.  This?  Right here?  It's the closest we're about to get to communicating directly with a passenger.''



``\emph{I understand},'' Defiant said.  ``\emph{But that's enough.}''



``They're passengers?'' I asked.



``The shell?  No.  The outer shell, the concept, the \emph{execution, }they're tapping into religious metaphors.  The devil, the serpent, the angel, buddha, mother earth, the maiden, each connected in turn to fundamental \emph{forces}.  Flame, water, fate, time, earth, the \emph{self}.  Things deep-seated and fundamental to their creator's belief system, because that's how the passengers interpret our world.  Through \emph{us}.  But deep down?  Beyond that surface, beyond the basic programming that drives them to do what they've been doing for thirty years?  It's the passenger's brush strokes.  And I'm \emph{getting} to her.''



``\emph{No you're not},'' Defiant said.  ``\emph{Because you're stopping now.}''



``Fuck that,'' Tattletale said.



``You're stopping now because it \emph{worked}.''



One by one, the monitors throughout the Dragonfly shifted, until the one at the very front was the only one that still showed the Simurgh.



The Dragonfly changed course as we looked at the scene that was showing on every other monitor.



The Azazel, airborne.  D.T. officers within were standing by the windows, while one with a camera was holding it above their heads, aiming it towards the window, pointed at the water.



A dark mass was beneath.



Leviathan, matching pace with the ship.



The Dragonfly and Pendragon broke from their orbit around the Simurgh.



The Simurgh followed.



\sectionbreak



The Y\`{a}ngb\v{a}n tore through the settlement, barely visible, as fast as arrows loosed from a bow.



One set of powers to give them speed, another to give them the ability to create crude images, illusions, blurry and indistinct.



A weak power, but far less so when coupled with the fact that they were making \emph{themselves} just as blurry and indistinct.  To top it off, they were making themselves invisible for fractions of a second, and they were lashing out with short blades of cutting energy when they reappeared, slicing through the Australian refugees.



Bombs went off, coordinated, ripping through the spaces the Y\`{a}ngb\v{a}n had already passed through, cleaning up the ones who'd survived, killing the rescue personnel who were trying to save lives.



Earth Tav, barely two million people spread out across the globe, with this being the largest population center, based around the portal that Faultline, Labyrinth and Scrub had erected.



Without this base for supplies and communication, the other settlements would falter.  Disease would be crippling, food would be scarce at best.



And the Y\`{a}ngb\v{a}n would no doubt reap the rewards, claiming the planet for the C.U.I.



The Pendragon led the way through the portal, and it suffered the brunt of the bombs that the Y\`{a}ngb\v{a}n had left in their wake, no doubt to stop any reinforcements.



The Pendragon sank, no longer fully airborne, and the Dragonfly's cameras could see as Golem, Vista and Cuff did what they could to patch it together.



Not enough.  It landed, \emph{hard}.



Another bomb went off as the Pendragon hit ground.  Had the Y\`{a}ngb\v{a}n plotted that?  A second line of defense?



``Everyone okay?'' I asked.



``\emph{Give us a minute.  Nobody dead.}``



At least the Pendragon was a combat ship, meant to take a beating.  If the Dragonfly had been the first one through, we would have been obliterated.  At \emph{best}, we'd have managed to evacuate with parachutes, flight packs and shadow-form powers.



We passed through the area the Pendragon had cleared.  One small ship against what had to be thirty Y\`{a}ngb\v{a}n members.  They didn't move, but \emph{flickered}, existing as scarce smudges and streaks of black and an odd midnight blue from the regions of their heads.  They cast out more smudges in matching colors with their image generation powers, turned invisible for one or two seconds at a time when they saw opportunities to catch refugees off guard.  Some merely killed.  Others slashed at eyes or ears, removed hands.  Butchered.



What would the C.U.I. want with scores of butchered people?



It wasn't \emph{really} the fault of the individual Y\`{a}ngb\v{a}n members.  They were brainwashed, subsumed into this collective of shared powers, their identities erased.



But that didn't make their actions \emph{forgivable}.



The Simurgh followed behind the Dragonfly, moving each wing until it was pointed straight behind her as she sailed through the narrow, oddly-shaped portal.



When she unfolded her wings, extending each until a veritable halo of them surrounded her, a complete circle, I could feel my heart skip a beat.



``We need to give her orders,'' Tattletale said.



I nodded, mustering my swarm into a group large enough to communicate.



But there was no need.  She flew past us.



The singing had died down, but it welled up at full strength.  I almost staggered.



Rubble began to peel away from the demolished settlement beneath us.  Metal, bombs, pieces of structures.



As she reached less damaged areas, she picked up construction vehicles.



The fragments of metal around her were like a dense cloud, almost obscuring her, massive wings and all.



The singing increased in pitch.



A bomb detonated in the midst of the storm of debris, breaking up a bulldozer in the process.



Below her, the scene had gone still.  Y\`{a}ngb\v{a}n raider and civilian alike had gone still.  The smudges consolidated into forms.



Not the same Y\`{a}ngb\v{a}n I'd encountered before.  These ones wore similar outfits, but there were bodysuits beneath, no bare skin.  The multifaceted gem designs that covered their faces were dark blue, their costumes black.



Infiltrators.  A sub-set.  One of five sub-groups, apparently.



The debris settled into a single shape, drawing together.  Nothing welded, nothing screwed in together.  Merely a crude device, held together by telekinesis.



A fat, snub-nosed cannon, twice as long as she was tall.  She fired it, and the resulting \emph{bullet} was nearly ten feet across, a sphere of hot metal.



It crashed into a trio of Y\`{a}ngb\v{a}n.



She used her telekinesis to sweep it off to the right.  The misshapen bullet was compressed into a rough sphere in the time it took to soar down a long road, smashing through two members of the Y\`{a}ngb\v{a}n.  A bystander was clipped, spinning violently before collapsing in a heap.  Shattered arm and ribs, if not dead.



I bit my lip.



``\emph{Don't injure civilians},'' I communicated through the swarm.



She gave no sign she'd listened.  Her telekinesis grabbed four members of the Y\`{a}ngb\v{a}n who'd gotten too close, lifting them by their costumes or by some other debris that had surrounded them.



As if launched by catapults, they flew straight up, where they disappeared into the clouds above.



I winced as the screaming increased in intensity by another notch.



Did she \emph{have} to do that?



I felt a touch of paranoia, not just at the idea, but at the fact that I'd been concerned.  Paranoia over the fact I was feeling paranoid.



The Simurgh had crafted another gun.  They floated around her like satellites, firing only in those intermittent moments when she'd formed and loaded the necessary ammunition.



``\emph{Those are my guns},'' Kid Win reported over the comms.  ``\emph{Bigger, but mine.}``



I didn't like that she was screaming.  It set an ugly tone to this whole venture.



I \emph{really} didn't like that we couldn't direct her that well.  We were ending this confrontation decisively, we were \emph{probably} even doing it more cleanly and with less damage to civilians than there would be if we'd handled it ourselves.



But we'd brought the Simurgh here and people were getting hurt as collateral damage.  That was on us, everything else aside.



``I\ldots don't know what to feel right now,'' Imp said.



``It doesn't feel good,'' I said.



``I wish I knew what I'd said that got her on board,'' Tattletale said.  ``I went with the shotgun approach, trying to see what stuck\ldots and now I don't know what to leverage if we need to do it again.''



``You're so \emph{whiny},'' Rachel said.  ``You say we need her help, we got it.  Good.  Maybe now we can \emph{fight}.''



``Mm,'' Lung grunted.  ``This is true.  But I've seen what happens if you do something like \emph{this}, something big, and you fall.  You fall hard.''



I nodded at that.  ``Wise words, Lung.  Well said.''



``Do not talk to me,'' he rumbled.



I only shook my head.



``Fuck me, you guys are serious?''  Shadow Stalker murmured.  ``This is \emph{good}?  This is \emph{luck.  }There's a reason I stick to my fists and my crossbow.  They're reliable.  This Endbringer thing most definitely \emph{isn't}.''



``Of course it isn't,'' I said.  ``But you know that whole saying, finding a boyfriend?  Young, smart, wealthy, pick two?  We don't get to pick \emph{two}, here.  Options at the end of the world: clean, safe, effective, pick \emph{one}.''



``We got Bohu, but she doesn't move fast at all,'' Tattletale said.  ``Leviathan's on his way to pay the Elite a visit.  Collateral damage could be ugly there.''



``It isn't sustainable,'' I said.  ``Somehow, I don't think they're going to sit still if we ask them to.  What happens if we run out of enemies to attack?  If we need to put Leviathan to work and there aren't any targets that don't involve even \emph{more} collateral damage than we'll see when he attacks the Elite?''



``People are going to fall in line damn fast,'' Tattletale said.



``Probably,'' I said.  ``Or they'll run for the hills.''



``Win-win,'' Tattletale said.  ``We \emph{were} saying we needed people to split up more.''



The Simurgh opened fire, striking out with three guns, striking a neighborhood that had already been reduced to dust and flame by a series of bomb blasts.



``Somehow,'' Imp commented, ``This doesn't scream win-win to me.''



I nodded.



``Nothing saying this isn't another clever plan, set up to fuck with us, destroy our last shreds of hope,'' I said.



The Y\`{a}ngb\v{a}n were opening fire.  Projectiles that moved slowly, splitting in the air until there was a virtual storm of them.  Had they been aimed at the Dragonfly, we wouldn't have been able to dodge.  The Simurgh flew between the bullets like they weren't even a concern.  Debris blocked the shots.



In the midst of her maneuvering, she drew together a third gun from the storm of debris.



Then she somersaulted, heels over head as she rapidly shifted direction.



In the moment it took her to build acceleration, she looked directly at the camera.



Directly at \emph{me}.



She'd heard me, she understood, and she had responded.





