





\emph{At least she's stopped screaming}.



The Simurgh floated in the air, remaining in a kind of stasis, much like she'd been in when we'd approached her, but there was an entire rig of devices surrounding her.  A halo, almost, studded with guns and cannons at regular intervals.  The sky behind her was overcast, clouds rolling past us with the strong winds, and mingled dust and smoke slowly shifting beneath her, brown-gray.  The juxtaposition was eerie, the clouds of the sky moving faster than the smoke and dust, and the Simurgh between the two, utterly still.



On TV, back in the days when we'd \emph{had} television, there had been the various talk shows, news segments and interviews where the Endbringers would come up.  I'd listened, even though television wasn't really my thing.  I'd heard people theorize on the Simurgh's scream, wondering out loud about just how many of the disasters that followed in her wake were \emph{her}, and how many were our own overblown paranoia.



It helped to remind myself that I wasn't the only one who was debating the possibilities.  I'd listened for too long.  Was I tainted?  If this was all a trap, then I might already be seeded with some destructive or disastrous impulse.  Should I be hypervigilant?  Should I not stress over it?



It was a debate \emph{millions} of individuals had maintained amongst themselves, in the wake of the Simurgh's attacks.  Invariably, there wasn't a right answer.  If she wanted to fuck with me, there wasn't anything I could do.  Anything could and would fit into her game plan.



It wasn't just me, either.  I was \emph{very }aware of Lung's presence, and of Shadow Stalker's.



The Y\`{a}ngb\v{a}n were dealt with.  There were two major raiding parties, if we judged solely by the colors of their masks, and three or four other sub-groups tasked with different functions.  One raiding party was annihilated, and I could hope the Endbringer's presence would scare off the other group.



There was an upside of sorts, in that the Y\`{a}ngb\v{a}n didn't have access to Cauldron's doormaking parahuman.  It meant they moved exclusively through the portals that dotted Earth Bet, the same portals the refugees had used, which some stragglers were still using.  Various factions and governments were gathering small armies at each of the remaining portals.  One Earth was already lost to us, destroyed by Scion in the first day he'd been traveling universes.  The South American refugees who had fled through there would be either eradicated or reduced to such a small population that it barely mattered.  Earth Zayin, too, was gone, subsumed by the Sleeper.



Still, a dozen Earths remained, with people scattered all over them.  The C.U.I. had claimed one, and they'd be ready for retaliation, maintaining a defensive line.



I doubted that defensive line would hold if an Endbringer decided to march through.  No, they would be gathering their forces in anticipation of a possible attack.  \emph{Good}.



I took in my surroundings.  One ramshackle settlement, more than half of it obliterated by bombs.  Relatively little in the way of collateral damage on the Simurgh's part.



Psychological damage?  Quite possible.  The Simurgh was a terror weapon, her very \emph{presence} enough to rout armies, and these refugees weren't an army.  Morale had been low to start with.



I sighed.  We'd scared people off, and they'd fled to the hills, quite literally.  In a movie, this would have been the moment that people slowly began returning, the orchestral music swelling as they overcame their fear.



Ridiculous, in context.  They'd hide for \emph{days}, and they'd flee the second they saw the Simurgh again.



This wasn't a case where we'd be able to stop the imminent threat and then recruit a select few people from among the survivors.



``Yo,'' Tattletale said.  She had to run to get up the last stretch of the little hill that overlooked Tav's primary settlement.



``Yo,'' I responded.



``Total deadpan?  You can be a \emph{little} excited,'' she said.



``I am.  Quiet terror is a kind of excitement, isn't it?  Pulse pounding, heart in my throat, and I'm so tense I'm getting a headache, because I'm almost afraid to \emph{think}.''



``You think I'm \emph{not}?  \emph{Fuck}.  There's very few things that genuinely terrify me.  One of them is hanging out right above us, building something, and I can't even read her, which makes her one of the few things out there that \emph{surprise }me.''



Building something?  I looked up.



True enough, the Simurgh had her hands in front of her, and was manipulating debris in between her hands.



``What is she-''



`I \emph{don't know},'' Tattletale said, interrupting me.  ``What do you want me to do?  \emph{Ask} her?''



I shook my head.  ``How are the Pendragon's occupants doing?''



``Ship shape, but Defiant's wanting to be careful.  He's demanding they get triple-checked.  Kind of funny, seeing that from him.''



I shrugged.  It would be a bigger leap for Tattletale to see the changes in him than for me to see it.  I'd been acquainted with him over the past two years, while she only saw him here and there.



``They'll be up for it if we have a fight?'' I asked.



Tattletale shrugged.  ``For sure.  Scratches, bruises, but that's about it.  We're down to fight at a moment's notice.  Sad thing is, the worst thing Scion could do to us is wait a month or two before he comes back.''



``True,'' I agreed.



Not a pleasant thought.  If he took a leave of absence while we were trying to wrangle the Endbringers, odds were we'd get taken out by other factions or by the Endbringers themselves.



``I dunno,'' Imp said.  I managed to not be startled as she appeared.  ``Killing us all is pretty awful.''



``Awful, but not awful in the `let humanity destroy itself' sort of way,'' I pointed out.  ``Let us come up with a plan for fighting back, then disappearing?  Letting that plan fester and fuck us over?''



Imp shrugged.  ``So?  What do we do?''



``Handle what we can,'' I said.  ``Let's go talk to the others and hash out a plan of action.''



The three of us made our way down the hill to the settlement.  In the doing, we passed through a darker patch where the Simurgh's wingspan blocked out a portion of the sun.  What little sunlight could pass through the cloud cover, anyways.  I glanced up and saw her in shadow, the light behind her outlining her body, hair, feathers and the halo of improvised weapons.



Defiant had his helmet off.  His hair had grown in just a little, but wasn't much more than a buzz cut, stubble on one side of his face was much the same.  But for the lack of stubble on his cheek, I might not have noticed his face was partially a prosthetic.  A gift from the Nine.



``It worked,'' he said.



``More or less,'' I responded.  ``One civilian death and seven civilian injuries in the fighting, the death and two of the injuries were the Simurgh's fault.''



``Only that many,'' Defiant said.



``She was letting us know she \emph{could},'' Tattletale said.  ``Which is something we really should pay attention to, so long as we're trying to make sense of Endbringer psychology.  I'm wondering if you could say that they're primarily a warped super-ego, devoid of any real \emph{ego} or advanced \emph{id}.  Built in codes and rulesets, not human social rules, but still rules established by a creator.''



``Sigmund Freud,'' Defiant said.  ``I remember being back in University.  Second year psychology elective.  The professor said one word, `\emph{Freud}`, and the entire auditorium of students exploded in laughter.''



Tattletale smiled.  ``You're calling my analysis into question?''



``If you're basing it on the Freudian structural model, yes.''



``Freud was big on the whole Oedipus, Electra thing.  Mommy issues, daddy issues.  I'd say if we have any understanding of the Endbringers at all, there's definitely \emph{something} going on there.  Not \emph{sexual}, but you get what I mean.''



``You're \emph{way} overstating my intelligence,'' Imp said.  ``I don't get what you mean at all.''



``The Endbringers have a fucked up connection with whoever made them,'' I said.  ``Be it Eidolon or someone else.''



``I understand \emph{that}.''



``So if they're unmoored from whatever's anchoring them to reality,'' Tattletale said, ``What's motivating them \emph{now}?''



``A better question,'' I said, ``Is\ldots well, who the fuck is she following?''



``Us,'' Imp said.  ``You guys are overthinking this.''



I sighed.  ``She \emph{is} following us, probably.  Leviathan was following the Azazel, Simurgh followed the Dragonfly.  Both maintained consistent speeds, matching pace, keeping a short distance.  What I'm asking is, which of us, exactly, does the Simurgh follow?''



``Who's in control of her, for the time being?''  Tattletale summed up the question.



``There's an easy way to check that,'' Defiant murmured.  Odd, that his voice had a vaguely mechanical twang to it even with his helmet off.  ``Each person that was on the Dragonfly walks in a different direction, and we see who she follows.''



I frowned, glancing skyward for a moment.  No sign of any movement or response from the Simurgh.



``What?'' Tattletale asked.



``I wouldn't say anyone's in control of her,'' I said.  ``Because I don't think \emph{anyone} is in control of her except \emph{her, }and-''



I stopped there.



``\emph{What}?'' Tattletale asked, again.



``When she was first attacking the settlement and I was musing aloud at the possibility of betrayal, she very deliberately \emph{looked} at me.  It was a communication, all on its lonesome.  Letting me know the whole betrayal thing \emph{was} a possibility, that she had some self-volition, and letting me know she was listening.''



``We know she hears.  We know she's aware of everything around her, present or future.  Simurgh S.O.P.,'' Tattletale said.



``I know,'' I said.  ``But I'm not just saying she \emph{heard} me.  I'm saying she was \emph{listening}.  She's hearing every word we say here and she's paying attention to all of it, processing it, \emph{applying} it, maybe.''



``You may be reading too much into a momentary eye contact,'' Defiant said.  ``I'm watching the video footage in question right now\ldots yes.  I see what you're talking about.''



``Right?'' I asked.  ``So you agree?''



But he shook his head.  ``I suspect It's a bad sign if you're getting paranoid over this.  It's counterproductive, and the moment your fear or second-guessing is detrimental enough, you need to step down and walk away.''



I took a deep breath, then sighed.  ``I'm fine.''



``If there's an issue\ldots''



``No issue.  All I'm saying, the only reason I brought this up, is because I don't want to get on her bad side.  I'd very much appreciate it if we treated her with due respect.  Let's \emph{not} upset her by talking about her in a negative light.  Electra complexes, talking about who's controlling her, or experimenting on her.  I don't think it's that easy to understand her, and we're only going to upset her if we keep going down that road.''



``She doesn't get upset,'' Defiant said.  ``Didn't we just spend an inordinate amount of time talking about how Endbringers don't have conventional emotions?''



``Better safe than sorry,'' I said.



``Yes,'' he sighed the word.  ``Yes.  Of course.  I'm mentally exhausted, I'm being stubborn.''



``We're all mentally exhausted,'' I said.  I glanced up at the Simurgh.  ``Keep that in mind.''



There were nods all around.



``The Pendragon won't fly until I fix it,'' Defiant said, standing.  He pulled on his helmet, and there was an audible sound as it locked into place.  ``I'll need parts from elsewhere.  It also means leaving some people behind.  You can't fit everyone into the Dragonfly.''



``We'll do something low-risk in the meantime, then,'' I said.  ``Reduced group.''



``Sensible.  I'll go see after the others, then.  This would be a good time to eat, stock up on supplies or use the facilities.''



Defiant wasn't one for goodbyes or formalities.  He said he'd leave, and he left, his boots making heavy sounds with each footfall.



``Well, I'm going to go make water,'' Tattletale said, jerking a thumb towards one of the outhouses.  ``I'd be all girl-code and invite you with, but I actually like you guys, and I don't want to subject you to that \emph{atmosphere}.''



``Thanks,'' I said.



When Tattletale had disappeared, Imp and I sort of meandered over towards the others.



Canary was closest, helmet off, her hair plastered to her head with sweat, making her feathers that much more prominent where they stuck out of her hairline.



``This is crazy,'' she said.



``This is a \emph{Tuesday }for us,'' Imp replied, overly casual in a way that was almost forced.



I saw the dawning alarm on Canary's features.  I hurried to reassure her, ``It's really \emph{not}.  Ignore her.''



Canary nodded.



``Holding up okay?''  I asked.



``Pretty much.  There's one thing, but it\ldots it's pretty trivially stupid in the grand scheme of things.''



``We're killing time while we wait to get organized,'' I said.  ``Go ahead.''



``There were two people I was talking to.  Forget their names.  One's really forgettable and the other's obscure.''



``Foil and Parian,'' I said.



``Yes.  Right, yeah.  I was talking to them, and we had a lot in common, and then they went from warm to ice cold in a flash.  Couldn't understand why.''



I frowned.  ``That doesn't sound like either of them.''



``They didn't really say anything.  They just talked about going somewhere, and I asked if I could come, and they looked at me like I had three heads.''



``They probably wanted to be alone,'' I said.



``Yeah.  I get that,'' Canary said.



``\emph{Alone} alone,'' Imp responded.  ``End of the world, making every minute count?  Nudge, nudge, wink wink?''



Imp held her mask in one hand, using it to nudge Canary twice, then tipping it to the side as she winked, keeping time with the four words.



Canary's eyes went wide.  ``Oh.  \emph{Oh!''}



``Dudette, with all the hugging and reassuring they were doing, how was this even in question?''



``I don't follow the cape scene.  I don't know how close teammates get.  I just figured, shitty situation, life and death, maybe you cling tighter to any buoy in a storm\ldots oh god.  I asked if I could \emph{come with} them.''



Imp nodded sagely.  ``I can see where you'd get confused.  We're very close, here, after all.''



Canary was blushing, humiliated, the pink of her skin contrasting her yellow hair.



Imp continued, ``After all, Skitter\ldots \emph{Weaver} and I\ldots well\ldots''



She tried to make bedroom eyes at me, holding her hands in front of her, twisting her arms as she drew her shoulders forward, the very picture of a lovestruck schoolgirl.



Canary's face reddened further as Imp continued to poke fun.



Imp, for her part, gave it up after only two or three seconds.  ``Fuck.  Can't do it.  Weaver here has diddled my brother, and it just feels squick and incestuous.''



``\emph{That's }the reason we haven't ever done the relationship thing,'' I said, my voice flat.  ``It'd be weird in an almost incestuous way.''



Imp cackled.  One of very few people I knew who could \emph{cackle}.  She was enjoying herself.  This was her medium.  One of them.  ``You'd do better with Tattletale, or Rachel.''



``Thank you,'' I said, and I injected a little more sarcasm into my voice, ``for the mental pictures that evokes.''



She cackled again.



Eager to change the topic, I glanced at the others.  The Wards were sitting a short distance away, Kid Win, Golem, Vista and Cuff, sitting together.  Cuff was fixing up Golem's costume.



I'd feel weird about approaching them.  Technically, I was still a Ward, though my eighteenth birthday had come and gone.  I \emph{should} have moved up to the Protectorate, but I'd never been sworn in, had never filled in the paperwork.



The Slaughterhouse Nine, Scion and the mass-evacuation from Earth Bet sort of gave me an excuse, but I still didn't want to face the questions.



I glanced at Saint, who was sitting between Narwhal and Miss Militia.  They were pretty clearly talking guns.



Lung stood alone.  He was holding a skewer with meat all along the length.  A glance around didn't show any possible source.



A check with my swarm \emph{did}.  A few hundred feet away, there was a cooking fire that had gone out in the aftermath of the Y\`{a}ngb\v{a}n attack.  Lung had apparently claimed some food as a matter of course.



``Lung,'' I said, almost absently.



``You know him?'' Canary asked.



``Yeah,'' I said.



``He was kind of notorious in the Birdcage.  A lot of people, they come in, and they do something to make a statement.  Kill someone, pick someone suitable and \emph{claim} them, challenge someone suitably impressive to a fight, that sort of thing.''



``What did Lung do?'' I asked.



``He marched into the women's side of the prison, killed his underling, and then killed and maimed a bunch of others before the cell block leaders ordered people to pull back.  I got called into a meeting, too, where a bunch of people in charge of cell blocks asked me to come and tell them what I knew about him, since we arrived at the same time.''



I nodded.  ``But you didn't know anything.''



``No.  I think some of them were \emph{really} worried, too.  I thought they were going to hurt me, until Lustrum, uh, my cell block leader, backed me up, gave me her protection.''



``Geez,'' Imp said.  ``That's messed up.''



Canary shrugged.  ``How did you put it?  A \emph{Tuesday}?  A Tuesday in the Birdcage.''



``No, I'm not talking about \emph{that},'' Imp said.  ``I'm talking about the fact that Lustrum the feminazi was in charge of your cell block and you \emph{still} didn't pick up on the thing between Parian and Foil.  Isn't that, like, Sappho central?''



\emph{Sappho?}



Canary blushed again.  ``I\ldots uh.''



``I mean, \emph{seriously},'' Imp said.



``Ease up,'' I warned her.



``I\ldots I live and let live,'' Canary said.  ``I just didn't want to step on toes.''



``And you never got any?''



``I had somebody, but like I said\ldots''



They were still going as I focused on my swarm.  I gave some commands to the Dragonfly, which I had landed a mile and a half out of town, and brought it our way.



With the relay bugs, I could sense most of the settlement, the surrounding landscape, everything above and below.  That was only using half of them.



The remainder were fertilized, bearing eggs.



I'd flipped the switches, shifted them into breeding mode, and I was working on keeping them warm and well fed.  I'd have to wait until the eggs hatched before I found out whether the young had any range extension ability.  If I had to wait until they were adult, well, the world might end before I got that far.



Defiant was returning.  I stepped away from Canary and Imp to greet him.



``Let's go,'' he said.



\blacksquare



Smaller team, while the \emph{Pendragon }was out of action, smaller job.



The ones who were grounded would be looking after the settlement, ensuring the survivors were able to make it through the next few nights.



Tattletale was with me.  Imp and Rachel had come with for much the same reason Lung had.  They were restless personalities, unwilling to relax when there was a possibility of a conflict.  I wanted to think that Rachel's intentions were a little kinder in nature than Lung's, that she wanted to protect her friends, but I wasn't going to ask, nor was I going to set any hopes on it.



A pleasant idea, nothing more.



Lung was eerily quiet.  He'd acted to stop Shadow Stalker from attacking me, but he hadn't shown a glimmer of his power.



After we'd decided who went where, before we'd left, Canary had found a moment to talk to me.  To finish what she'd been about to say when Imp had interrupted to poke fun at her.



Information about Lung.



\emph{He coasted on reputation for some time.  Didn't use his power, didn't fight, just intimidated.  Nobody was willing to start something because nobody really knew what he was about.  Until this guy from Brockton Bay came in.  Had some info.  Except, by then, Lung was entrenched in Marquis' cell block, and even if someone wanted to go after him, they didn't want to deal with Marquis in the process.}



Lung hadn't been using his power.  Why?  Was there a reason?



A deep seated concern about his passenger, maybe?  No.  What would excuse that?



I needed to ask Tattletale, now that I knew, but there hadn't been a moment where we'd both been alone.



We had Shadow Stalker, who had no interest in rebuilding and resettling.  Defiant was with us as well, relying on remote monitoring to perform the occasional check-in on Saint.  Narwhal would manage the rest.



Miss Militia had come along, and nobody had said anything to mark it as fact, but I got the distinct impression it was for \emph{Defiant}\emph{`s }sake.



And, of course, we had the Simurgh.  Following.  She'd finished building what she'd been working on as she hovered over the aftermath of the fight at the Tav settlement.



A shortsword, four feet long, without any guard to protect the hand from an enemy's weapon, both sides of the blade serrated.  Black.



Defiant had called it a \emph{Gladius}.



Defiant had the cockpit and Miss Militia's company, and so I was left to hang out in the cabin, with Rachel sleeping beside me, Bastard and Huntress sleeping at her feet.



I admired her ability to rest in such stressful situations.  I glanced at Shadow Stalker, who seemed to be filled with nervous energy.  When we'd kidnapped her for Regent to control, Rachel had been able to sleep then, too.



I felt like I had to be \emph{responsible}, somehow.  I'd taken on three very dangerous individuals, with reputations ranging from bloodthirsty vigilante to \emph{Endbringer}, and I knew I'd blame myself if something went wrong on any count.  I couldn't sleep when there was information to take in, when there were people to watch, people to watch \emph{over, }and personalities to keep in check.



Threats and conflicts, within and without.



Many of the monitors were focused on Bohu, the towering Endbringer, tall enough that her heads reached the cloud cover.  Five \emph{miles} tall, give or take.  Gaunt, expressionless, without legs to walk with.  No, she moved like a block of stone that someone was pushing, not with lurching movements, but a steady, grinding progression that left bulldozed terrain in her wake.  Overlapping rings marked the area she traveled as well, as she continued switching between her typical combat-mode cycles, altering the terrain, raising walls, creating traps and deadfalls, generating architecture.



The monitors abruptly changed.  One shaky image, from one cameraman at just the right vantage point.



A golden streak crossing the evening sky, appearing out of nowhere.



Just about everyone in the Dragonfly tensed.  I felt myself draw in a breath, my meager chest swelling as if I could draw in confidence as well as air, preparing to give orders, to provide the call to arms.



But the golden light disappeared as soon as it had appeared.  Like the jet stream of an aircraft passing overhead, except it was \emph{light}, not smoke, and it only marked a brief period where he'd passed through our world on his way to other things.



We relaxed.



Rachel hadn't even woken up.  She was exhausted, though we'd barely participated in any fighting.



The Dragonfly moved closer to the ground as we approached the next portal.  It was squatter, broader, allowing for more ground traffic at a moment's notice, though it made the passage of flying vehicles more difficult.



Like Scion, exiting one world, passing through Bet on our way to the next.  It reminded me of my discussion with Panacea.  People who build and people who destroy.  We were trying to do the former, Scion the latter.



The Dragonfly passed through the portal.



Heavy rain showered down around us.  The Dragonfly faltered for an instant as it changed settings, very nearly nosediving into the ground beneath us.



Defiant pulled the craft up.



\emph{Agnes Court}, I thought.  I'd studied all of the major players in anticipation of the end of the world, I knew who the Elite were, and I knew who had built this.



She fit somewhere between Labyrinth and the Y\`{a}ngb\v{a}n's Ziggurat.  Organically grown structures.  Seeds that swelled into pillars, stairs, houses and bigger things, given enough time in proximity to their master.  The wood-like substance hardened to stone of varying colors after she terminated the growth.



In the span of two and a half days, she'd grown a walled city, one with an elaborate castle at the northmost end, with shelters and what looked like a sewer system, if I was judging the perfectly round hole in the cliff face below right.  It was \emph{gushing} water.



Two days to make this.



Leviathan had taken less than an hour to demolish it.



The wall, taller than some skyscrapers, was shattered in three places, damaged enough to serve little purpose in others.  A shallow river flowed through the spots where the damage to the wall reached the ground.



Leviathan had perched himself atop the castle's highest tower, though the tower wasn't broad enough for him to put anything more than two clawed hands and two feet on the very top.  His tail wound around the structure, in one window and out another.



Even through the rain, his five eyes glowed.



``Oh no,'' I said.  ``The civilians.  The refugees.''



``Relatively few,'' Tattletale said.  ``That's\ldots yeah.  I don't think we offed people in any substantial numbers.''



\emph{In any substantial numbers}, I thought.



``I didn't think they'd get this kind of structure up in time,'' I said.



``Court grows things exponentially, given time,'' Tattletale said.



She frowned.



``\emph{Grew} things exponentially.''



If that was the case, then we'd lost a possible asset.  Fuck this, fuck the Elite for bringing things to this point.



``There were a thousand people here,'' Defiant said.  ``Many who were managing supplies and resources for the rebuilding and resettlement efforts.''



``I'd explain,'' Tattletale said, ``But I'd rather not explain twice.''



``Twice?''  Miss Militia asked.



Tattletale pointed.



The \emph{Azazel }had parked on top of a tower at the wall's edge, almost opposite to where Leviathan was.  A crowd had gathered around it.



Too many to be just the Dragon's Teeth.  Far too many.



I swallowed.



Cameras zoomed in on the individuals.  Hard to make out through the rain, but I could draw the appropriate conclusions.



The Dragonfly landed, far gentler in the process than I would have managed on my own.



``Time to face the music,'' Tattletale said.



I took the time to restructure my costume, raising my hood to protect my head before I stepped out into the pouring rain.  Defiant was in step to my right, Tattletale to my left.



No, not \emph{pouring}.  Pounding.  As heavy a rainfall as I'd ever experienced.



The other major players had arrived.  The \emph{Thanda}, Faultline, the Irregulars, the Meisters, the remnants of the Suits\ldots  Cauldron.



It took time for everyone from the Dragonfly to make their way outside.  We looked so small in comparison to the group arrayed before us.  People had disappeared here and there.  Dead or gone in the wake of the disaster on the oil rig, or the fighting that had followed.



Even after we'd arrived, after the ramp had closed, the group before us remained utterly silent.  There was only the sound of the rain, so deafening I might have been unable to hear people if they'd \emph{shouted}.  I clenched my fists, tried not to shiver.  If I started, I wouldn't stop.  Staying calm, staying confident, my attention on my bugs as a way of escaping the stresses here\ldots it made for an almost zen moment.



It was in that same moment that the Simurgh descended.



Descended was the wrong word.  She \emph{fell}.  It was as though she'd stopped lifting herself into the air, and let herself drop.  Her wings moved to control her descent, keep her facing towards the ground as she plummeted.  In the gloom of the rain and the heavy stormclouds above, her silver-white body was the easiest thing to make out.  If the assembled capes hadn't already been keeping a wary eye on her, the movement would have turned heads anyways.



A white streak, plummeting from the sky, striking Leviathan.



The shockwave that accompanied the impact tore through the tower.  Superficial features broke away first, followed by the internal structures that had provided structural integrity.  The end result was a gradual, almost slow-motion collapse, a lingering view of the Simurgh and Leviathan as they'd been at the moment of impact.



They tilted as the tower did, but neither Endbringer moved.  The Simurgh had both feet pressed against Leviathan's stomach, one hand reaching up to grip his face, the other hand holding the gladius she'd made, buried so deep in Leviathan's sternum that only a little bit of the handle stuck out.



Pieces of her halo began to fall, including her fabricated guns and the other debris she'd arranged to form the ring itself.  It rained down like a localized meteor shower, striking the castle, the base of the tower, the wall, and Leviathan.



The Simurgh managed to avoid being struck, even with her vast wingspan.  She leaped up, kicking herself off of Leviathan, and found a perch on the wall, folding her wings around herself and the top of the wall, as if to ward off the worst of the rain.



Maybe six or seven seconds later, the tower finished collapsing, and Leviathan's massive, dense body hit ground, crashing through several buildings before settling, the handle of the sword still sticking out of the wound.



He didn't rise.  He twitched, lashed out with his tail, dashing three already tattered buildings to smithereens, then gushed with water, producing four or five times his body weight in water without even moving.



Death throes?



She'd hit his \emph{core}.



Beside me, Imp wiped at the lenses of her mask, tried again, and then pulled it off entirely.  She stared at the scene with her mouth agape, then looked to Tattletale, mouthing three words in a voice too quiet to make out through the pounding rain.



Tattletale's hair was soaked through, streaming with rivulets of water that ran down her back.  Dark makeup ran from the eye sockets of her costume.



However bedraggled she appeared, just after a minute of standing in the rain, she also looked contemplative, rubbing her chin as she hugged her other arm close for warmth.



Leviathan went utterly still.



I watched the faces of the others.  Every set of eyes was fixed on Leviathan's body.  Nobody seemed like they were willing or able to tear their eyes away from the scene.



Slowly, almost at a glacial pace, Leviathan moved.  One hand with the disproportionately long claws was planted on the ground, then another.  His tail provided some of the support and strength to leverage himself to his feet.



\emph{That}, oddly enough, seemed to surprise Tattletale.  Her hand dropped from her face to her side.  She fumbled to hook her thumb over her belt as if she needed the extra leverage.



When Leviathan had pulled himself to an upright position with both feet beneath him, his head hanging down, the tail snaked around the handle of the sword.



He wrenched it free, and tore out chunks of his own chest in the process.  There was little left but the handle and the base of the sword.  Needle-like lengths of metal speared out from the base, but the bulk of the sword's material was gone.



Leviathan continued to move with an almost excruciating slowness as he reached out with his claws, extending each arm to his sides, like a figure crucified.



The wound was superficial, but he was acting like he'd received a more grievous wound than any of \emph{us} had dealt in the past.



The wind turned, and the wall ceased to provide a curtain against the rain.  For a moment, Leviathan was only a silhouette.



I could see his shape distort.



Others reacted before I saw anything different.  The Number Man, Tattletale, Dinah, Faultline\ldots they saw something I couldn't make out through the curtains of torrential rain.  The Number Man said something to Doctor Mother, and I saw Dinah fall back just an instant before Faultline gave a hand signal to her crew.  They adopted fighting stances.



Did they \emph{really} think we could fight, if it came down to it?  Against \emph{two} Endbringers?



It was maybe twenty seconds of stillness, seeing only vague shapes through the shifting downpour, before the wind turned again.  I got a glimpse of what the Simurgh had done.



I could hear a squeak from beside me.  I expected it to be Imp, saw it was Shadow Stalker, instead.  She clutched her crossbow in both hands.



Fins.  Leviathan had fins.



They were like blades, points sweeping backwards.  A fin rooted in the side of his arm, from wrist to elbow, the point scything back.  Had it not been limp enough to trail on the ground, it might have reached his shoulder.  More at the sides of his neck and along the length of his spine, forming an almost serrated pattern where multiple fins overlapped.  Perhaps some at his legs.  The fins ran down the length of his tail, and ended in a cluster at the end, like the tuft of fur at the end of a lion's tail, exaggerated many times over in size.



He flexed a claw, and I could see webbing between each finger, mottled in black and an iridescent green that matched his eyes.  It made me think of the bioluminescence of a jellyfish in the deep ocean.



In synchronous motions, the Simurgh unfurled her wings, stretching them to their full length, and Leviathan flexed his fins, letting them unfold in kind.  Each fin was the same as the webbing, mottled black and a eerie green, and the echo-image of water that accompanied his movement produced \emph{mist} as it washed over the fins.  It obscured him almost completely, and as much as the pouring rain served to drive it away, the rainwater produced more mist as it touched the fins.



It took some time to clear, and even then, it only cleared because Leviathan had folded the fins up again.  When we could see Leviathan again, he had collapsed into a sitting position, one overlong arm draped over his legs, `chin' resting on one shoulder, completely at ease.



Above him, the Simurgh slowly folded her wings closed, like a reversal of a flower blossoming.



Doctor Mother turned to face us.



``Wha-  The-'' she stuttered.



Contessa, holding an umbrella to keep the both of them dry, set an arm on the Doctor's shoulder.  The Doctor fell silent, stopping only to look at Leviathan, then turned back to Tattletale.



Tattletale managed a grin.  ``I'd say there's a silver lining in all this, but that phrase has sort of lost it's cachet over the last decade or so.''



She gestured in the vague direction of the Simurgh before hugging her arms against her body.  ``\ldotsHe's probably stronger, which helps if he's going up against Scion, right?''



``I think,'' Doctor Mother said.  She paused very deliberately.  ``It would be very wise to keep the Endbringers \emph{separated}from here on out.''



``We might have to fight them, before or after we take on Scion,'' King of Swords, leader of one division of the Suits voiced the concerns that everyone was harboring.



Lung was the next one to speak.  ``What did she do?''



``Upgraded Leviathan,'' Tattletale said.  ``Attuned some device to the right frequency or setting, then tapped into his core without doing too much harm to Leviathan.  Fed things into there.  Knowledge, data, nanotechnology.''



Defiant's head turned, as if Tattletale had said something.



``Yeah,'' Tattletale said.  ``Nanotech.  Why do you think the fins were turning water to mist?''



``\emph{My} tech?''  Defiant asked.



``Among one or two other advancements.  If the density rules are in effect, I'd bet those fins are just as hard to cut through as Leviathan's arm or torso.  Disintegration effect, maybe something else.''



``Mecha-Leviathan?'' Imp murmured.



``That's not- it doesn't fit with what we know of them,'' Defiant said.



Tattletale spread her arms, a massive, exaggerated `\emph{who knows?}` gesture.



``It's the fucking Simurgh,'' Rachel said.



``I hope you can understand why we're\ldots \emph{distressed} with you,'' the Doctor said.



``\emph{Fuck you},'' Tattletale retorted.  ``Cope.''



I put my hand on her shoulder.  She didn't relent, nor did she release any of her tension.



``You wiped out two defending forces,'' the Doctor said.  ``We lost the Y\`{a}ngb\v{a}n's support when you took out their infiltration squads, and the Elite are wiped out.''



I squeezed Tattletale's shoulder.  She gave me an annoyed look, but she backed away.



I took in a deep breath.  I could see the Doctor fold her arms.  Like a mother or schoolteacher awaiting an apology from the recalcitrant student.



``Fuck you,'' I said.



``You don't want us for enemies,'' the Doctor said.



``We have the fucking Simu-'' Imp started.  Tattletale elbowed her.



``The Y\`{a}ngb\v{a}n were doing more harm than good,'' I said.



``They were limiting their strikes to civilians.  Not something I agree with, but with Earth, with \emph{every} Earth on the line, I'd forego two or three thousand lives for the help of over two hundred of the C.U.I.'s trained parahumans.''



``They'd \emph{given up},'' Tattletale said.  ``They were taking territory to run and hide.''



``Contessa would have changed their minds.''



Tattletale shrugged.  ``Don't blame us for not taking your plans into account, when you don't \emph{share} your plans with anyone.''



``This is common sense.  No matter.  The \emph{Elite}, though?''



``They were attacking civilians.''



``They were nonviolent.  Refugees in the vicinity of the portal were evacuated.  The Elite then made contact with possible settlers who they thought would be interested in paying a premium for good shelter, for resources and supplies.  If not paying with cash, then paying with \emph{skills}.  Doctors, talented artists, scholars\ldots it was one of our best bets for re-establishing a hub of development across all of the Earths.''



``They broke the truce,'' Tattletale said.



``Again, they were an \emph{asset}.  They were cooperating.  The truce hardly stands in this dark hour.''



``They broke the truce,'' I echoed Tattletale.  ``The code has been there since the beginning.  If a bigger threat shows up, we band together.  We don't distract each other with attacks or murder attempts, we don't take advantage of the situation to fuck with \emph{civilians}.  The truce is there for a \emph{reason}, and it has weight because everyone knows that they can't handle the trouble that gets express-delivered to their doorsteps when they've defied it.''



``Siding with Endbringers could be seen as a violation,'' Queen of Wands said.  ``I seem to recall \emph{you} participated in an effort to drive out a gang that had escalated too much, too violently, too fast.''



Her eyes fell on Lung.



Were they \emph{serious}?



``Don't be fucking stupid,'' Faultline said.  ``If you start going after the Undersiders and Guild for trying to amass enough firepower to take down \emph{Scion}, then \emph{nobody's }going to be able to put up a fight.''



``Hey,'' Tattletale said.  ``Faultline, sticking up for me?  This is a first.''



``So you agree with this?  Using the Endbringers?''  one of the Thanda asked.



Tattletale grinned.  ``Agree?  It was \emph{her} idea.''



Faultline whipped her head around.  ``\emph{No}.  No it wasn't.''



``Talking to the monsters.  Well, you said talk to \emph{Scion}, but this is close.  You can have partial credit.''



``I'll have no such thing.  I don't \emph{disagree} with this, but I won't condone it either.  This is the Undersider's plan, they can reap the consequences if it goes wrong.''



Tattletale smiled, but it wasn't quite a \emph{grin}.  Confident, calm.  I doubted anyone but the perception thinkers on the other side could see, but Tattletale was clenching her jaw in an effort to keep her teeth from chattering.



I felt just a little warmer, owing to my hood.  I spoke so Tattletale wouldn't have to try and risk an ill-timed chattering of teeth.  ``That's fair.  We'll deal with the consequences, be it a stab in the back from the Endbringers or punishment that follows from any \emph{real} issues that follow from this.  But we \emph{will} keep going after anyone who violates the truce.''



Rachel stepped forward, her arm pressing against my shoulder and side, as if she was bolstering me with physical presence.  Through the bugs I'd planted on him, I could sense Lung folding his arms.



``You will not be taking charge of \emph{all} of the Endbringers,'' the Doctor said.  ``Teacher emerged with a small force at his disposal.  He defeated the Protectorate squads that were deployed at one empty location\ldots''



``The place Khonsu or Tohu were supposed to appear,'' Tattletale said.



``Quite.  It was Khonsu.  The Endbringer has imprinted on Teacher's group, and he has offered to sell that squad, along with the Endbringer, to a sufficiently wealthy buyer.  We agreed, if only to keep this from becoming a \emph{monopoly }on Endbringers.''



Tattletale smiled a little, but didn't talk.



``How good of you,'' Defiant said.



``We \emph{strongly} advise you leave Tohu for another party to claim,'' the Doctor said.  ``Focus on the three you have.''



Defiant glanced at Tattletale and I.  I looked at Tattletale, reading her expression, before coming to a conclusion.  ``That's fine.''



``Then we're one step closer to a resolution,'' the Doctor said.  ``Much better than the alternative.''



Veiled threats, now?  Just how badly had we fucked her plans?



``This is more firepower than we expected to have at this juncture,'' the Doctor said.  ``But not enough by itself.  Without sufficient distraction, Scion will treat the Endbringers as he treated Behemoth.  We'll step forward and unveil our own plan B and plan C at the time of battle.''



``Armies,'' Tattletale said.  ``You were collecting people for a reason, and you didn't release every Case Fifty-three you made.''



``Essentially,'' the Doctor said.



``Five groups,'' I said, and my eyes fell on Dinah, who was standing beside Faultline.  ``We should split up so we can respond the \emph{instant} Scion appears.  We make sure every group has some way to maybe occupy him or pin him down, and we move to reinforce.''



Dinah, standing beside Faultline, nodded slowly.



``Four Endbringers, and then Dragon and Teacher to comprise the final group,'' the Doctor said.  ``If Tohu arrives, she can reinforce the weakest group.  Quite possibly Bohu.''



``Yes,'' Defiant said.  He was clutching his spear so tight I thought it would break.  He looked to Miss Militia for clarification.



``I'll run it by Chevalier,'' she said, ``But I don't see a problem with this.''



There were heads nodding.



\emph{Not enough.  We don't have enough people here.  There's groups missing.  People still hiding}.  \emph{People like the Y\`{a}ngb\v{a}n who are fighting us instead of helping.}



I was all too aware of the Simurgh and Leviathan at the corner of my peripheral vision, of Lung and Shadow Stalker, who I could sense with my swarm.



\emph{Too many people ready to stab us in the back.}



``I would recommend,'' the Doctor said, speaking slowly, ``That you take your time to visit loved ones, say goodbyes and make your peace.  I don't think there will be another fight after this.''





