





``So this is it,'' Tattletale murmured.



``Just about,'' I said.



``You ready?'' Tattletale asked.



I shook my head.  I sighed, and glanced out over the fields of grass.  So much beautiful nature.  So many \emph{worlds} to explore, now, each subtly different, each with its own hidden treasures.  But even a field of tall grass had an art to it.



For an instant, I felt a kind of pull.  The same sort of intrusive thought that made one think, `what if I stepped off the edge of this cliff?' or `what if I opened the car door right now and threw myself into traffic?'  Not suicidal thoughts, but thoughts that were clear enough and alarming enough that we worried we might listen of our own accord.



\emph{What if I just left?  Walked away}\emph{?}



I only needed to travel a short distance away for a short time.  It would be \emph{so} quiet.  No sound, people or artificial lights.  No pressure, no imminent danger.



I couldn't think of the last time I'd truly enjoyed quiet.  I'd experienced it when I'd flown out over the ocean.  I'd never been a people person, and I'd spent so much time in the midst of a crowd.  I'd been around the Undersiders, then I'd been in the midst of my territory.  From there to jail, from jail to the Wards.



From the Wards to a small war with inter-global stakes.



Solitude had a pull.  I was an introvert by nature, and I felt so \emph{drained}.  A little while by myself, to recharge my batteries, to \emph{think}.  Me and now-distant storm clouds, fields of grass, trees and water crashing against cliff faces far below.



What worried me was the idea that I'd get caught up in that gravity.  It had happened when I flew out alone, before.  If I left to recuperate, to get centered and try to think of something I could do\ldots could I say with confidence that I'd come back?  Would I fail to come up with any idea, and simply\ldots stay until it was too late?



Was that cowardly?  Was it a mark against me if I couldn't say for certain?  Or was it like how a person could be courageous at the same time they were utterly terrified?  I wasn't terrified, wasn't about to flee.  I had reasons for fighting\ldots but a part of me definitely liked the notion of going.  Of not fighting.  Surviving up until Scion passed through this Earth and then dying in a flash, possibly unawares.



I clenched my teeth.



All a fantasy, anyways.  There was a tether keeping me here.  Several tethers.



Rachel scratched Huntress' neck as she approached me.  She stopped right next to me, then bumped me with her arm.  A push, enough that I had to move my foot to keep my balance.



We stood there, my arm pressing against her arm, her attention on Huntress and Bastard, as the two canines vied for her attention.  I couldn't articulate how much I appreciated it, didn't want to look at her or do anything that might be misinterpreted as discomfort.



One tether.



``Reminds me of the movies I used to watch,'' Imp commented.  ``On the shitty kid's channels, at noon on Saturdays.  My mom would be too out of it from the night before to want the TV, so I'd have to watch with the volume turned down and sit, like, three feet away from the screen.  But I could usually get a good two or three hours of brain-rotting TV-watching in before I got kicked out of the apartment.  Best part of my week, for \emph{years}.''



``You're rambling,'' Tattletale admonished.



``Anyways, this is kind of like the movies where you have the stray dog the kid found and the first owner, and it's the end of the movie and they're both calling to see who the dog is willing to come to.''



``That's the fucking stupidest thing I ever heard of,'' Rachel said.



Imp only grinned.  ``And the dog starts going one way, until the bad owner does something like bring a choke chain out of his pocket, gets out the riding crop he used to beat the dog in the beginning of the movie, or or says a fatally stupid line, like, `come on, my precious money machine.'  And the dog gives the abusive owner a final fuck you, peeing on him before going back to the kid, or something like that.''



``My precious money machine,'' I echoed Imp.  ``Really?''



``You know what I mean.  Just that line that signals, `\emph{I'm so evil.'}''



``Be better if the dog tore out the abusive asshole's throat,'' Rachel said.



``That'd be \emph{so fucking}\emph{awesome},'' Imp said, grinning.  ``I went through this phase where, you know, I sort of wanted a movie to change it up.  Catch the kids off guard, show them that, hey, the good guy doesn't always win.  Got to the point I was getting depressed after watching those happy flicks.  Then my mom's new boyfriend Lonnie got her `cleaned up', and she started waking up on Saturday mornings, and that was it.  No more movie time for Aisha.  Never got back into it.''



``That's too bad,'' I murmured.  \emph{Where the hell is she going with this}?



Imp paused, frowning.  ``\emph{Fucking} Lonnie.  Anyways, I remember wanting the dog to go back to the first owner, and like, that'd be it.  Movie over.  Bad end.  Life doesn't always fucking work out peachy.''



``Doesn't,'' Rachel said.  ``But I'd probably stop watching movies if I saw an ending like that.''



``We're \emph{rambling},'' Tattletale repeated herself.  ``And I'm suddenly feeling Grue's absence.  He'd keep us in order, here.''



Imp gave Tattletale an annoyed look.  ``Anyways, this is kind of like that, isn't it?  Like the kids begging and pleading for the dog to follow them.  Except not.''



``The opposite,'' Rachel said.



``The \emph{reverse}, yes,'' Tattletale corrected.  ``Yeah.  Well, let's get this over with.''



Rachel got on top of Huntress' back, and I activated my flight pack.  Imp mounted Bastard, while Tattletale mounted a dog I didn't know.  The same dog Bitch had lent to me while we were mobilizing to go after the Nine.  Each of us moved in different directions.



High above us, the Simurgh turned.  With the innumerable wings that extended behind her, she was capable of a surprising amount of finesse and expression.  There was an aggression apparent if her wings were fully extended, with only the tips drawn slightly forward, like a claw with the points extended forward.  There was a outward focus when she flexed her wings to their limits, as if she were watching, observing.  Conversely, she was capable of introspection, of focus on a single thing, her wings all folded in.  All the while, her expression was neutral, her gaze cold.



I wasn't going to underestimate her, though.  Too easy for all of that to be a bluff.



When she moved, it was almost careless.  Two of her three largest wings unfurled as if she were waving a hand dismissively, aiming that gesture at the \emph{world}.  She turned in the air, then threw every wing back behind her, driving herself forward.



Well, we knew who she was following.



``Fuck me,'' I could hear Tattletale muttering with the bugs I'd planted on her.  The Simurgh came to a stop directly above her.  She repeated herself, as if for emphasis.  ``\emph{Fuck me}.''



I felt my heart sink.



Some of that was on Tattletale's behalf.  Of course the Simurgh had picked her to follow.  Tattletale had done the talking.  Tattletale was a thinker, just like the Simurgh.  She was the de-facto leader of the Undersiders, in many respects.



But a small part of me had hoped that the Simurgh had picked \emph{me} to follow.  That same part of me had almost believed it, taken it for granted.  It was horrible and scary and almost \emph{wrong}, having an Endbringer at one's beck and call, but I'd been prepared to shoulder the burden.  I \emph{wanted} to handle it, so people I cared about wouldn't have to.



Another part of me?  Maybe it had wanted her to be stuck to me, just to have one more tether keeping me connected, at a point where I felt like I wasn't very connected at all.



And perhaps I wanted it to have the power so close to hand, so I could be \emph{relevant}.



Humanity was being wiped out, settlement by settlement.  Continents rendered uninhabitable, ecosystems demolished, weather patterns shifting.  Our opponent was nigh-untouchable, capable of crossing between different Earths like we crossed a room, and we barely \emph{understood} him.



And here I was.  Strip away all of the pretense, the reputation, the connections and the image, take off the mask, and I was only a girl with the ability to control bugs.  A hundred and thirty pounds.



I'd bemoaned my innate limitations before, but I'd never felt them as a crushing pressure in the way I felt it now.



The shock of seeing the Simurgh pick Tattletale had thrown me.  I forced myself to take a deep breath and get centered.  I turned to the relaxation techniques Jessica Yamada had taught me.



Tattletale needed support, and I couldn't discount the idea that this was just the Simurgh being the Simurgh.  Explicitly or instinctively fucking with our heads.



We collected as a group again.  The dogs turned around and slowly made their way back.



I saw Tattletale's expression as she looked at me.  The lines of worry in her forehead that she tried to mask with a raised eyebrow, the feigned confidence, the lopsided grin.



I knew she read me ten times as well.  The little shifts in her expression as she glanced at my hands, at my face.  There was no doubt in my mind that she was reading me like a book.  She knew every train of thought that had just crossed my mind, the worries, the anxieties, the shameful fact that I'd \emph{wanted} the Simurgh to follow me.



Her lopsided grin widened just a little, but there was sympathy in her expression.



``Guess I'm going to hold the fort,'' she said.  ``Probably makes the most sense, really.  You guys go.  Do what Narwhal said.''



There were nods from Imp and Rachel.



``You know the drill, Scotty,'' Imp said.  ``Take me home.''



``Yeah,'' Rachel added.



Two portals opened.



They passed through.  I stayed in place.



``I could stay with you,'' I said.



``You \emph{could},'' Tattletale said.



``But?'' I asked.



``I don't think you \emph{should}, and I don't think you \emph{can. } Go.''



``Tattletale\ldots Lisa--''



``I'll be fine.  I've got \emph{her} for company.''  Tattletale pointed skyward.  The Simurgh had collected her guns and built several others.  The halo of individual components was now almost entirely made up of guns in varying sizes.  They were arranged in a careful formation, so the small guns marked the spaces between the large ones, and the largest gun barrels and nozzles radiated outward like the rays from a star.



I gave Tattletale a dubious look, she only grinned.



``I'll be here,'' she promised.  ``Go.  Like Narwhal said, get your affairs in order.''



I didn't budge.  Instead I looked to the fields of grass again.  It took me a second to figure out why one patch was darker than the rest.  Then I remembered the Simurgh.  She was casting a shadow.



``Realistic.  We agreed to go down fighting, right?''



``Right,'' I said, turning back to Tattletale.



She shrugged.  ``But we're going down.  Let's not pretend, because that little self-delusion isn't going to hold up when push comes to shove.  Better to focus our energy on believing that we're going to get wiped out, but we'll take that motherfucker down with us.''



\emph{Not exactly the most encouraging sentiment.}



``I'm\ldots not so pessimistic,'' I said.  ``I think we can take him down, and we can do it without getting completely annihilated in the process.''



``There we go.  That's the attitude I was looking for.''



I stared at her.



Was she bluffing?  Hiding something?



``You know something,'' I said.



``I know \emph{lots} of stuff.''



``And you're deflecting.  What are you keeping from me?''



``Not just you,'' she said.  Tattletale sighed.  ``It's not helpful.''



``Tell me.''



``I thought you wanted blissful ignorance.''



``Time for that is past.  Might as well share.''



Tattletale frowned.  ``Contessa's power.''



``It's telling her victory is impossible?'' I asked.



``No.  Well, maybe.  I don't know.  Haven't exactly had a long conversation with her.  No.  I'm saying\ldots well\ldots Scion has it.  Her power.  That line he fed Eidolon?  It was calculated to devastate the man at the point he was flying highest, so the fall would be more catastrophic.  It's something \emph{I} couldn't pull off.  I watched some footage of the fight, where Scion's power didn't nix the cameras.  Corroborates the evidence.  He wasn't actively using the power, but there's a confidence there.''



``Scion sees the path to victory?''



``Or something close.''



``You're sure?''



``The evidence, his attitude, as far as he has any attitude at all\ldots yeah.  None of the limitations like Contessa has, I don't think.  No blind spots.  Just\ldots yeah.''



I nodded.  The wind was making a magnificent sound where it ran through the grass, punctuated by the crashes of waves far below us.  A flock of tiny brown birds took flight from the midst of the fields.   They deliberately avoided the Simurgh, as though there was a bubble around her that they refused to pass through.



``You have my complete and total permission,'' Tattletale said, ``to swear a little.  Swear a lot.  You're doing this thing where you're going distant.  It's not like your body language isn't hard enough to read anyways, but you're lost in thought, and I figured you'd be flipping out.''



``I don't really flip out.''



``You, um--''



I knew what she was thinking about.  It was almost a relief to find we were still on the same page, after all this time apart.  I understood her, she understood me.  We were friends.



Her thoughts were on Alexandria and Tagg.  The point where I'd killed them had also been the same point that I'd taken leave from the Undersiders.  Joined the other side.



``I don't flip out on or around my friends,'' I said.



``I'm telling you he knows how to beat us.  He only has to reach for that one power, and he's got a solution to whatever we throw at him.''



``Every power has a weakness,'' I said.



``A power that lets you win automatically is kind of hard to circumvent.''



``Hard, but not impossible,'' I said.  ``Is it odd that I almost feel more \emph{optimistic}?''



``Yes.  Exceedingly,'' Tattletale said.  She cocked her head a little to one side.  It was something I'd seen her do before, as if she was a bird, trying to see things from a different angle.  ``What are you thinking?''



I shook my head.  ``Nothing.  But\ldots some of the best powers we've gone up against have had pretty fatal weaknesses.  When we went up against Butcher, her having fourteen consciousnesses to draw on might not have helped a ton when she was trying to deal with Cherish's ability.  We used Echidna's ability to absorb dead matter and grow to trap her in Coil's base.  Bought ourselves time.''



``I \emph{think} Scion's schtick is that he doesn't have fatal flaws.  We got our powers because they gave them out.  He \emph{crippled} the powers, so we wouldn't be able to fight back if it came down to it.  Crippled yours, limiting you to bugs, crippled mine by limiting my ability to analyze them.  He started all this because he \emph{was certain} it would work, used that path to victory to map it all out.  Wondered if we'd fight back, then mapped out a path where he'd have enough power to take humanity on in every conceivable scenario.''



``Then we create an inconceivable scenario,'' I said.



``\emph{How?}''



I shook my head.  ``Don't know.  But I'd like to think the Endbringers won't fit into his grand plan.''



``Not enough,'' Tattletale said.



``Cauldron too.''



She shook her head, a little too forcefully.  Strands of her blonde hair fell across her face.  ``They've caused as many problems as they've fixed.''



Something in that, in the way she was almost too preoccupied to fix her hair, it flicked a switch in my head.  A warning bell.  I was already stepping forward in response.



``Tattletale,'' I said, interrupting her before she could speak again.  I grabbed her hand with both of mine.  ``Stop.''



She froze, like a deer in the headlights.



``Stop,'' I said, again.  I pulled her into a hug.



The negativity mingled with the bravado\ldots I hadn't picked up on it.  Hadn't truly understood my friend.  She was \emph{scared, }and she'd been hiding it.



She stood there, the bridge of her nose hard against my collarbone, and I was reminded again of how she was shorter than me.



``Attacks that pretty much penetrate any defense,'' she mumbled.  ``We have yet to \emph{really} hurt him.  Mobile.  Perceptions are out there.  And he \emph{wins}.  He gets victory as a power.''



``There are options.  There are \emph{always} options.  Ways to circumvent powers, ways to trip him up.  He really didn't like it when I created multiple swarm decoys.  When \emph{anyone} duplicated.  Maybe there's a clue in there.''



``Maybe,'' Tattletale mumbled.  I could feel her fingernails against the fabric of my suit, at my back.  ``\emph{Fuck }this.  I hate feeling so \emph{dumb}.  So much shit I don't know, shit I \emph{can't} know.  Like fucking \emph{Ziz} here.  Fuck, I've barely ever given a crap about anyone except myself and my friends, and now I'm fucking caring what happens to \emph{everyone}, when I can't do \emph{anything} about it.''



I held on.  I could have gone on, told her that there were ways to cheat.  That, with all the powers in the world, there had to be ways to cheat.  But she didn't need reassurances.



She was a master of bluffing, wore a mask better than anyone I knew, and she'd adopted her \emph{persona} in a way that nobody else in the Undersiders or Wards had.  In the midst of all of this, she'd been a pillar, a source that everyone had been turning to when they had questions.



But where was someone in that position supposed to turn to when they needed support?



A minute passed before she broke away.  She turned her back to me before I could see her face.



``All good?'' I asked.



``Peachy,'' she said, without looking at me.  She stretched, then wiped at her eyes.  ``smudged my makeup, where I painted my eyelids black inside my mask, smearing it across your shoulder.''



I played along.  ``I always liked the lenses.  The goggles, if you want to call them that.''



``Sure, but you can't have too many people with the lenses on the same team, or you look like you've got a \emph{theme}, and only the lame-ass teams do that.''



I smiled a little.



She looked up, ``\emph{You }don't say a word about this to anyone.  Morons are going to get the wrong idea if they hear we were hugging.  \emph{Way} overactive imaginations.''



\emph{Talking to the Simurgh}?



She turned around, and I was momentarily confused.  Her makeup \emph{was} smudged in a way that suggested it had been smeared by my costume.  No signs of the running makeup that had followed the rain at the Elite's court, no sign of tears.



She smiled a little, conspiratorially.



``You and the Simurgh are a good fit after all,'' I said.  ``Fucking with people's heads.''



``We'll see.  Now, I think it's time you stop babysitting me.''



I frowned.



``Come hang out later, if you don't find anything more pressing.  Which you probably will.  I'll be okay, now I've got something figured out.  Something to look for.  Plus I should get back to looking after Dragon's stuff.  Reams of shit to cover.''



I nodded.



``Go,'' she said.



I went.  There was a gravity here of its own.  If I didn't go now, I wouldn't go at all.



The introvert, seeking out people, and the extrovert left with only a silent Endbringer for company.



\emph{I'll be back soon}, I thought.



\sectionbreak



``I want to pet her.''



``\emph{My} turn!''



I could sense them with my bugs before I'd even approached.  A cluster of kids, an adult woman, a fenced-in area, a small furry animal.



I didn't want to intrude, so I reached out and gathered a swarm of butterflies.



They stirred, gathering in a small, localized storm.



``What?  \emph{Oh}.  Skit- Weaver's coming,'' Charlotte said.



I held back on using the flight pack, walking instead.  Wouldn't do to use up too much charge, in case I found myself having to fight at a moment's notice.



The cottage was one of the outposts that Tattletale's crews had put together.  North end of town, overlooking the spot that would have been the boat graveyard, a forty minute walk from the Brockton Bay settlement.



Three stories tall, hidden from plain view by a line of trees and a short hill, the cottage had a small fenced-in area next to it.  Three dogs stood guard.



They growled at my approach.  I didn't flinch or slow down, and the growling intensified.



``Hush,'' Charlotte said.  ``Stand down.''



The growling stopped.



I approached, and Charlotte gave me a hug.  She looked good, if maybe about five years older than she was.  She was dressed in a very utilitarian way, but I couldn't help but notice the gun she wore at her belt.



The kids, for their part, hung back, wary, staring.



I pulled off my mask, then rubbed at my face where it had been tightest.  I put on my glasses.



``How bad?'' Charlotte asked, her voice quiet.



``Hm?''  For an instant, I thought she'd mention my dad.



``The situation.''



Oh.  It was only \emph{that}.  ``The world's ending.  About as bad as it gets.''



She nodded.  ``You remember the kids?''



I did.  Two years older\emph{.  }Mai, Ephraim, Mason and Katy.  Aiden and Jessie were gone.  ``Hi guys.  Long time no see.''



They shuffled their feet.  Mai raised a hand in a shy wave, but that was it.



``It's not anything personal,'' Charlotte said.  ``You're famous, and we watched videos of you online.  The O.J. and-``



I groaned aloud.



Charlotte smiled a little.  ``All of the clips.  I wanted them to remember you somehow.''



With that, the kids seemed to get even \emph{more} shy, which only made me feel just as awkward.  My eye traveled over to the fenced-in area.  The fence looked like it had been made out of two different materials, one set layered over top of the other, attached with chain and cord.  Three baby goats were standing inside.



``Yeah.  Tattletale organized it so anyone who established a home could get goats to breed and milk.  If it comes down to it, a single goat goes a long way.  Milk, yogurt, cheese\ldots''  Charlotte glanced over her shoulder at the five kids, then whispered, ``\emph{Meat}.''



``Makes a lot of sense,'' I said.



I approached the fence and bent down, extending a hand for the goat.  When it didn't bite or retreat, I reached through to run my hand along its wiry coat.  Coarse hair.  It bleated at the touch, but didn't pull away.



I'd wanted to check in.  To see if they were doing okay.  They were.



Now I felt out of place.  So odd, considering this group had once been a fixture in my life.  I couldn't just leave, but I didn't know what to do now that I'd arrived.



``Lot of crazy rumors flying around,'' Charlotte said.



``All true, I suspect,'' I answered her.  \emph{I don't want to talk about that stuff.}



``Okay.''  There was no surprise in her voice, no questions.



``We've gathered our forces.  Scared the people who were causing problems.  The Y\`{a}ngb\v{a}n probably won't cause any more trouble.  The Elite won't be controlling access to key settlements, screening out people who have a right to be there.''



``You say that so matter-of-factly,'' Charlotte said.



``It was very matter-of-fact,'' I responded.  I stood, removing my hand from between the slats of the fence, turning to face her.



``Okay,'' she said, again.



Again, no questions.  No \emph{hunger} to know.



It would be unfair to tell her, to burden her with it.



But there wasn't a lot to talk about, once I got the cape stuff out of the way.  I watched the goats cavorting about.



``Diana, Bruce, and Habreham,''  Charlotte said.



``Habreham?''



``Mai named him.''



``Ah.''  I glanced at the kids, saw Mai with her arms folded, looking very stern as she nodded at me.  \emph{She could be very serious about being very silly}, I remembered.



They were all keeping their distance.  No smiles, no excitement at my approach.



What had I expected?  For some of them, I'd been gone for a third of their lives.



The kids perked up as the cottage's door opened.  Forrest stepped outside.  He'd ditched the tight jeans in favor of looser ones, and wore a simple, short-sleeved flannel shirt.  He'd kept the heavy beard.



He smiled as he approached, then shook my hand.  ``You're here to see if we took the deal?''



``Deal?''



He looked at Charlotte.  ``You didn't tell her?''



Charlotte shook her head.  ``I'm embarrassed.''



I glanced between them, searching for a hint.  ``Explain?''



``A group arrived, offering powers for sale.  They had \emph{crates} of these glass vials.''



``When?''



``An hour ago?''



\emph{After our discussion}, I thought.  Rachel, Imp, Tattletale and I had stopped to eat, to talk about our next step.  Cauldron had gone right to work.



``A black woman, lab coat?'' I asked.  ``White woman with dark hair, wearing a suit?''



Forrest nodded.



``We didn't take the deal,'' Charlotte said.  ``She sounded convincing, but\ldots I can't say why I didn't agree.  Because there were the kids to look after, and I'm not a fighter.''



``A \emph{lot} of people agreed,'' Forrest said.  ``It's a chance to do something, instead of sitting around being helpless.  But Charlotte and I talked it over, and we agreed it isn't for us.''



\emph{She said she doesn't know why she refused, but they talked it over}?



The statements didn't mesh.  Charlotte was avoiding my eye contact.



\emph{Me}?



Was \emph{I} the reason they'd refused?



My heart felt heavy in my chest, but I managed to keep it together, to sound confident as I spoke, ``I think it's probably a great deal easier to accept a deal like that when you haven't seen what capes deal with firsthand.''



``Yeah,'' Forrest said, and there was a note of relief in his voice that only confirmed my thoughts.



``I don't\ldots I've \emph{imagined} having powers, who hasn't?  But I couldn't\ldots \emph{have} them and not help\ldots and I don't think I could help,'' Charlotte said.



``I was in the neighborhood when Hookwolf's group attacked some guy's store, and then nothing affecting me personally for \emph{years}, until Leviathan attacked.  I was there when Mannequin attacked the Boardwalk.''



``I remember.''



I could remember Forrest grabbing the concrete block, hammering at Mannequin's head.  He'd cracked the casing, even, playing a pivotal role in Mannequin giving up.



``We talked about it, and neither one of us wants to leave the kids without a\ldots \emph{figure}?  I don't even know what we should call ourselves.  But I've seen how bad it gets when it's bad.  I \emph{want} to help, but I'm not sure I'd be better than the next guy when it came down to getting powers.''



I wasn't so sure he was right.  Forrest had been more courageous than some \emph{capes} I'd met.  He had a kind of conviction I was coming to connect to some of the best of us.  A conviction I wanted to imagine I had.



I realized I'd been silent too long, lost in thought.



``Okay.  No, no worries as far as the formula goes.  There's a chance it mutates you into a monster, anyways.''



``She mentioned that,'' Charlotte said.



``Yeah.  That's fine.  Better you didn't take it.  Just wanted to check in,'' I told them.  ``You have everything you need?''



``More than enough money,'' Charlotte said.  ``We're doing pretty well for supplies, too.  Thank you.''



I nodded.



I was feeling a kind of restlessness.  It had been there from the beginning, when I'd realized I was out of place, that I'd intruded on this domestic scene.  It was building, getting worse.



``Will it last the next while?'' I asked.  ``The money, the supplies?''



Forrest gave me a funny look.  ``A \emph{while}?  In what sense?''



``A decade?  Two decades?  Three?''



He didn't respond.  Instead, he gave me a very curious look.  I very nearly flinched.



``Yeah,'' Forrest said.  His voice was soft, almost gentle.  ``Enough to last us as long as we need.''



``Good,'' I said.



Funny, that the weather was so nice here.  The sudden changes from night to day, good weather to bad were going to wreak havoc on my ability to adjust or sleep.  It had all been so chaotic, was \emph{still} chaotic.



That probably wasn't going to end.



I heaved out a sigh, realized in the process that I'd been holding my breath.  ``Good.  That's all, really.  I just\ldots''



\emph{Needed a reminder about what I'm fighting for, before the last fight}.



``\ldots{}yeah.  That's all,'' I said.



Forrest extended a hand for me to shake.  I took it.



Charlotte gave me another hug.  I stepped away, then took flight.



Stupid, to fly when my fuel might run low, but I wasn't up to anything more.



I was \emph{just} out of earshot when my bugs caught Mai's voice, ``You said the money wasn't any good.''



``Shh.  \emph{Quiet},'' Charlotte hushed her.



``You \emph{did}.  You said nobody'll take it.  They only take barter.''



``Shhh,'' Charlotte said.



``And you said we're going to have a leaning winter if we don't get more vegetables out of the garden, so why'd you say we're doing okay?''



``Because we are,'' Forrest said.  Bugs I'd planted on his sleeve tracked his movement as he wrapped an arm around Charlotte's shoulders, pulling her close.



``We owe her everything,'' Charlotte said.  ``That's enough, in the big picture.''



She'd said it, no doubt, because she knew I could hear with my bugs.  She wasn't \emph{wily}, as people went, but I could believe it was for my benefit more than Mai's.



It still meant the world to me.



``Doorway, please,'' I said.  ``\emph{Faceti}.''



The portal opened in the air.



\sectionbreak



``Ms. Hebert,'' Glenn Chambers greeted me.  He smiled.  ``It must be the end of the world after all, my old students paying visits.''



``Students?'' I asked.  My eye traveled across the room to the man who sat at the opposite end of the desk.  Quinn Calle, my old lawyer.  He'd stood from his seat when I entered.



Mr. Chambers hadn't.  He leaned forward.  ``\emph{Weren't} you?  I'd like to think I taught something to everyone I worked with.  Maybe that's conceited.''



``Conceit is a good trait to have,'' I said.  ``An overblown sense of one's own abilities can be worthwhile, \emph{if} you're prepared to try to live up to it.''



Mr. Calle raised an eyebrow.  He was a little disheveled, having doffed both tie and suit jacket, and the makeup that de-emphasized the scar on his cheek was partially gone.  He glanced up as the lights flickered, then extended a hand.



I shook it.  ``Didn't expect to see you here.''



``A collaborative effort,'' he said.  Smooth, unruffled, despite his appearance.  ``Too much paperwork to sort through by myself, so I tracked down several people who've worked with supervillains.''



``Ah,'' I said.



``I make costumes for \emph{anyone},'' Glenn said.  ``But the PRT makes more costumes for heroes, and they've discouraged other heroes from using my services, due to hard feelings.  It left me with a fairly one-sided customer base.  Well, I do fashion as well, but that's proven to be more of a hobby than a paying venture.''



``Fashion and crime wouldn't connect, ordinarily, but Glenn does have a passing knowledge of the nation's rogue's gallery,'' Mr. Calle said.  ``PRT likes that he's keeping me from being \emph{too} forgiving with old clients.''



``What is it you're doing, exactly?''  I asked.



``Vetting capes,'' Mr. Calle said.  ``Not much work for a criminal lawyer in circumstances like these.  They found another job for me, helping decide who gets out of jail, when witnesses can't be found.  Who leaves the Birdcage, who gets out of conventional jails, and so on.  Starting from the highest power ratings, working our way down.''



\emph{Building up our forces}, I thought.  Cauldron passing around formulas like candy, guys like Calle releasing old prisoners.



What were the others doing?



``I just\ldots''



``You wanted to thank me,'' Glenn said.  ``Naturally.''



``Naturally,'' I said, my voice dry.



Mr. Calle spoke, arching his eyebrows.  ``Rest assured, I'm not hurt in the least, that you chose to thank him before you thanked me.  I mean, I was only the man who stood by and helped you through the system \emph{after} the ill-timed murder of Alexandria and Director Tagg, right in front of me, but yes.  The man who gives fashion  advice is a higher priority.''



I crossed the room, bent over and kissed Mr. Calle on the cheek.  ``Sorry.  I wasn't sure if you'd have hard feelings over that.  Thank you, for everything.''



``Quite welcome,'' he replied, almost absently.  His attention was on the laptop in front of him.



``It's refreshing, I admit,'' Glenn told me.  ``All of the others who've filed through have been telling me they had a last minute epiphany, that they realized the true import of what I had been trying to teach them about image and self-image.  Some of them might have even \emph{meant} it.''



``That may be optimistic,'' Mr. Calle said, without glancing up from his laptop.



``Probably.  But \emph{this} young lady took my words to heart \emph{before} the world started ending.  I could see it.''



``I didn't make a good hero, I'm afraid,'' I said.



``Somehow,'' Glenn said, leaning back in his seat, ``I'm not surprised.''



``Yes, fancy that,'' Mr. Calle said.  ``I would have thought you'd be a \emph{model} hero.''



``I \emph{did }try with her,'' Glenn said.  ``And, to her credit, she did try with herself too.  Stellar effort, but\ldots''



``I don't think this is a world where heroics work,'' I said.



Glenn looked genuinely annoyed.  ``Chevalier.''



``He's running the Protectorate from a hospital bed,'' I said.  ``And they're trying their best to keep Ingenue from visiting.  He's refusing to be healed until all of the other patients have been treated.''



``Clever,'' Glenn said.  ``Only way he'll be able to sit back and do his job.  The bosses can't order him to be a face for the public if he's confined to his bed.  Moment the battle starts, he'll accept a visit and be on the front lines, I guarantee you.''



``I figured it was something like that,'' I said.



``See?  Proving \emph{both} my points.  You were an excellent student, and Chevalier is exactly the kind of hero we need,'' Glenn said.  He looked up as an employee entered the room, dropping off a box of files.  ``Thank you, Carol.''



She glanced at me and Mr. Calle.  Mr. Calle, for his part, made a gun with his index finger and thumb, winking and clicking his tongue as he `shot' her.  She smiled, shaking her head.



``Really?''  Glenn asked.  ``Crass.''



Mr. Calle didn't take his eyes off the laptop.  ``I can be crass when I'm not with a client.''



``There's no need to be crass at all.''



``It \emph{works}.''



``\emph{Everything }works when you're good looking enough.  Which is, again, why there's no need to be crass.''



``Oh, but it's \emph{fun},'' Mr. Calle said.  ``We all have our vices, don't we?''



Glenn gave his stomach a pat, nodding sagely, ``I admit that's true.  I must admit a predilection for show tunes.''



``I'm starting to wonder how you guys get any work done,'' I said.



``You have to keep alert somehow,'' Glenn replied.  He turned his laptop around.  ``You know him.''



\emph{\"{U}ber.}



``I do, kind of.  I didn't think he'd get arrested.  What did \"{U}ber do?''



Mr. Calle answered for Glenn.  ``Attempted murder.  Bit of a loose cannon, but not so loose they'd stick him in the Birdcage.  Shacked up with Circus for a while, but it didn't take.  Relationship-wise or as a partnership.  They stood to lose more than they could ever gain if he got loose again, so they made it a secure facility.  He hasn't escaped.''



``Something happened to Leet,'' I concluded.  ``Only way he'd be that\ldots rudderless.''



``Crossed the wrong people, got offed,'' Glenn told me.



\emph{We could have used him}.



``\"{U}ber's\ldots he should have been better than he was,'' I said.  ``I remember thinking he'd have been a stellar cape if Leet hadn't been holding him down.''



``Apparently not,'' Glenn said.  ``Would you accept him or reject him?''



``Accept,'' I said.  ``But I'm biased.  I'll take pretty much anyone.  I took \emph{Lung}.''



``You took the Simurgh,'' Mr. Calle said, apparently unfazed.



``Yeah,'' I said.



``Enough said,'' he replied.



``Put \"{U}ber in a hospital.  Let him give medical attention.  Easy, move on to the next.''



Glenn sighed.  ``Until we accidentally release the one person psychotic enough to derail the entire defense effort.  I do seem to recall Chevalier, Tattletale and a\ldots.''



``Accord,'' I said.  ``Yeah, I get your point.''



Glenn smiled.  ``I \emph{have} missed talking with you.  There's no stopping and waiting for you to catch up with us.  Smart people are so few and far between.''



``So true,'' Mr. Calle said, including himself among the smart people without a moment's hesitation.



``Which means,'' Glenn said, ``I shouldn't act dense.  You came here for a reason, something that isn't thanking me.''



``I just\ldots I guess I wanted to say\ldots I'm a lot closer to figuring out who I am.  Where I fit.  A bit ago, I would have said I decided, but-``



``Doubt in the final moments,'' Glenn said.  ``Well, that's something I understand.''



``Mm hmm,'' Mr. Calle acknowledged him, agreeing.



``I've seen capes change their outside to reflect a new inside, after close calls and lifechanging events.  You're wondering where you stand, now that you're at the brink.  Only natural,'' Glenn said.



``Wholly \emph{unnatural},'' Mr. Calle said.  ``\emph{Most }change their tune when they get a slap in the face and a one-way ticket to the Birdcage.  Who's the \emph{real} individual, the man who they were for twenty years prior, or the man they become after the handcuffs go on?''



I asked, ``You're saying this me isn't the real me, that it's a product of the crisis?''



``You?  Hmm\ldots'' Mr. Calle paused.



``Her behavior after her arrest was remarkably in line with \emph{prior} behavior,'' Glenn commented.  ``Including the, as you describe it, \emph{poorly-timed} murder of two very notable figures, after she was provoked.  Essentially word for word what Miss Militia had put in her file.''



``Point conceded,'' Mr. Calle said.



``I'm not sure that's how I want to be defined,'' I said.



``Take it for what it is,'' Glenn said.  ``You're very scary when angry.  Perhaps\ldots now is the time to be angry?''



``Being angry at Scion is like raging against a natural disaster,'' I said.  ``It doesn't understand.  It doesn't react.  My screams are drowned out in the chaos.''



``You weren't screaming when you attacked Alexandria,'' Mr. Calle commented.  ``In fact, I remember you were very quiet.''



I nodded.



``If you've decided who you want to be,'' Glenn said, ``Accept \emph{all} of it.  The good, the bad, the ambiguous.  Vulnerabilities and strengths.  The anger, that's part of it.  The fear for people you care about, that's a strength too.  Doesn't feel very good while you're experiencing it, but it's a well you can tap.''



``Right,'' I said.  I thought of Charlotte and the kids.



Fuck, I didn't want to fail here, to let them lose what they were building.



``And with luck, knowing who you are means not having to waste time and effort on putting up a facade.  Maybe that extra time and effort you have at your disposal will make the difference.''



A portal opened behind me.  A member of the New York Wards.  A little bedraggled.



``Take care, Ms. Hebert,'' Mr. Calle told me.  Making it easier for me to take my leave, for the new arrival to step in.



``Goodbye,'' I said.  ``Thanks again.''



``Goodbye, Taylor,'' Glenn said.  ``You, Weaver, Skitter and the strategist all give him hell, understand?  For all of us who can't be on the front lines.''



I nodded.



``Doorway.  To Miss Militia.''



\sectionbreak



The doorway opened, and a small crowd shifted from around me, their attention elsewhere.



It took me a minute to figure out what I was seeing.  A hundred people, sitting on folding chairs or standing off in the grass to either side or behind the collection of chairs.  They were watching a movie that was being projected onto a massive white sheet, some holding paper bowls with soup, others holding beers.



My bugs moved over the crowd, and I located my teammates.



Parian and Foil in their civilian clothes, sitting together, holding hands.  I might have missed them, if not for the rapier that Foil was keeping close at hand.



Aisha, sitting next to Rachel, with the dogs under their seats where they'd be out of the way.  The Heartbroken were filling the seats immediately around them.  Eerie distortions of Alec, with different frames, hair colors, genders and fashion styles, but close enough for me to notice.



The movie showed a dog on screen, being chased by a group of kids.  I could see Imp's face in the dark, looking as pleased as Rachel appeared annoyed.



``\emph{It's not the same dog},'' Rachel hissed the words.  ``\emph{Why isn't anyone seeing that?  Same breed, but totally different dogs.}''



``\emph{Pretend},'' Aisha said, her smile not faltering in the slightest.



One of the younger Heartbroken shushed them.



I saw Miss Militia off to one side, with a group of kid capes.  Crucible, Kid Win, Vista, two more I didn't recognize, and Aiden.  The kids were watching the screen, while Miss Militia watched the crowd for trouble, with a fair bit of her attention being aimed at Aisha and Rachel.



I didn't want to interrupt, didn't want to spoil this for the kids.



It was a distraction.  A stupid movie, apparently, but a distraction.  For the capes, it was a chance to not think about what came next.  To not dwell on the fact that, a minute, an hour, a day or a week from now, we could be fighting with everything on the line.



I drew a small notepad from my belt, then a pen.



\emph{Miss Militia,}



\emph{Once upon a time, I wanted to be a hero.  On the night I changed my mind, the same night we attacked the fundraiser, I was going to write you a letter.  I suppose it's time I finish it\ldots}



\emph{It wasn't an easy letter to write then, and it's not any easier to write now, for very different reasons.  I wasn't a good hero, and I use the past tense there because I can't genuinely call myself a hero at this point.  I've been visiting people tonight, and I suspect I might visit others tomorrow if circumstances allow, thanking those who need thanking, making sure that maybe there's a legacy, someone to remember me if we all make it through this.}



\emph{When I was a hero, when I did it right, I think I was emulating you and Chevalier.  Looking back, I can imagine that maybe things would have turned out okay if I'd joined the Wards, because you would have had my back.  I can't say I regret what I've done, but I can't say I don't, either\ldots}



\emph{Sorry.  Don't let me waste your time.  All I wanted to say was thank you.  Thank you for having my back when it counted.}



\emph{– Taylor Hebert.}



I folded it up and gave it to my swarm to deliver.  I didn't wait to see her reaction before whispering, ``\emph{Doorway.  Tattletale.}''



\sectionbreak



Barely an hour spent, all in all, on running my errands, looking after people.



Not all of the people I should have contacted.  I'd left out some of the most important ones.



\emph{The }most important one.  My dad.



Perhaps I was a coward after all.  I knew the answer, I just didn't want to hear it.



I couldn't be absolutely positive I \emph{could} hear it.  I couldn't take a gut punch like that so close to such a crucial fight.



I was nearly silent as I made my way through the building.  Tattletale's soldiers acknowledged me as I passed.



Not her place.  Somewhere out of the way.  A secure building, quite possibly one only Cauldron could access.



I found out why as I entered Tattletale's room.  She was asleep, curled up on a couch with a laptop that had a black screen, glowing lightly.



I heard a murmur.  \emph{Mumbling in her sleep}?



I bent over her, saw the track where the black makeup she'd used to color in her eye sockets had run.  A tear, from the corner of one eye, down the side of her face.  Crying a little in her sleep.



I found a blanket and draped it over her, then sat on the edge of the couch.



``Nobody really left for me but you guys,'' I said.  ``Everyone else has moved on.''



Another murmur.



Not from Tattletale.



Not from any direction in particular.



I listened for it, and almost immediately wished I hadn't.



Music.  A lullaby, so quiet it was almost imperceptible.



I wasn't hearing it with my \emph{ears}.



I crossed the room, and my hand touched thick glass that was quite probably bulletproof.  I could see men standing guard outside, their night-vision visors glowing.



The Simurgh was outside.



The lullaby continued as she worked on expanding her arsenal.



``\emph{Stop},'' I whispered.



She stopped.



The silence was deafening.  No noise in the area, no wind, no people.



It made me wonder if the lullaby had been louder than I'd thought.  How was I supposed to gauge the volume of it when I had nothing to measure it against but my own thoughts?



\emph{I'm sorry}.



The words crossed my mind.  My voice.



Not my words.



The Simurgh turned, her hair flowing in the wind.  Her hands were still held up as she worked her telekinesis on yet another weapon to add to her arsenal.  Her eyes met mine.



I found my way back to the couch, sitting next to Tattletale.



I didn't sleep at all that night.





