





Study, analysis.



An impulse, something that couldn't be tracked with any conventional devices, then a steady feedback.  Pretercognition.  Spread out over several targets at once, it serves as her primary sense.  Each target is conceptualized in the context of twelve to eighty years of history.  More time, more feedback from the steady feed of information, and the images clarify.  Discard the useless elements, maintain the pivotal ones.



Deciphering, searching for the fulcrum points.



Focus on one target, and the decoding is faster, but this costs her the ability to sense other things in any detail.  Necessary, in most cases, to form a distraction, or to strike hard enough that she can take advantage of the enemy's preoccupation.



This was made easier by another sense.  Another power extends in the other direction, and this is not one that can be sensed by most.  Possibilities, as another jumble of images.  These clarify as the others do, as eventualities are discarded, the targets around her coming into focus.



One target comes into full focus, and their existence is now visible, from the moment of their birth until the time they disappear from sight.  Often, this is the point of their death.  Other times, they disappear into darkness, obscured by another power.



\emph{Often, }this is not a true obstacle, if she has had time to \emph{look}.  There are the fulcrum points.  Crises, themes, decisions, fears and aspirations are clearly visible.  The individual is understood well enough that their actions can be guessed after they disappear from view.



A stone is thrown into darkness.  It can be safely assumed that it will continue traveling until it hits something.



Frame a situation to put a target under optimal fear and stress.  Hormone secretions increase.  Manipulate situation to a position where they will connect familiar visual, olfactory and auditory cues to their immediate environment.  Place, smell, degree of stress, sights and sounds match fulcrum point.  Hormone secretions increase further.



The result is hallucinations, momentary or sustained.  Hearing sounds, seeing things, smelling something, where none truly exist.  Fight or flight response feeds need for escapism.  A hallucination serves as the first step into a daydream.



The stone is thrown.



She does this with people and the various secretions within their bodies, with machines and data, with the elements and simple cause and effect.



Her hibernation state serves to allow for collection of low-feedback information about the environment.  Feedback that cannot be tracked or sensed, collecting information over a series of passes.  The stone can be a series of billiard balls instead, one striking another, striking another in turn.  Diminishing returns with each target struck.



With study and careful precision, each ball can find its pocket.  Spheres of synthetic resin meet the furthest point of a ledge covered by woven wool, perching on the edge as they spend their momentum.  Almost, they remain there, not enough energy to pass over the precipice.  Then they fall.  Three disappear into oblivion in perfect synchronicity.



She does not feel joy at this.  This is the task.  Means to ends.



She is utterly blind in the present, with no eyesight or other senses to perceive things in the now.  No sight, no hearing, no touch or taste.  Not a crippling flaw, and a difficult flaw for others to use against her.  The present is only a fragment in a long span of time when one can see the past and future both.



But she faces an obstacle that she is utterly blind to, now.  No apparent past or future.  In interacting with it, she is limited to context.  She sees not the obstacle, but she can see things that are set in motion around it.  She cannot see it strike, but she can see the reaction, the aftermath.



She sees the stone fly out of the darkness, and she can determine where it was thrown from.



There is a task to be completed, but things must be set in place first.



An obstacle must be removed.  This is critical, but she is blind to it.  This is the greatest problem she faces.



She requires access to particular information.  This can be arranged by positioning targets carefully.



She requires resources.  This requires patience.  She will have access to them soon enough, provided things aren't cast into darkness by the obstacle.



She must be unmolested.  This is given freely to her.



She operates alongside the subjects.  This serves her aims on several fronts.  She communicates when she can with the others.  A current of water in a particular set of wavelengths, to her brother who sees the world as water – living things as balloons of meat largely made up of water, moisture in the air, moisture running over every available surface as he uses his abilities to move clouds and fog into place.



The younger siblings are harder to target, but their birthplace is studded with temporal anomalies.  Holes in time, wells, echoes, slowed time and accelerated time, from confrontations that have occurred, even confrontations she participated in.  She manipulates the wind as she affected the water.  A stirring that prompts another stirring, and the temporal effects that can be affected are struck in a particular pattern, strained in a particular order, from the fastest to the slowest.  Again, she repeats the process emphasizing the anomalies with individuals trapped within.  As communications go, it is crude, but she knows her siblings like she knows any other target.  Slow, calm, the subjects.



More communications, to get the point across.



The younger sister needs only a tremor, the very same wavelength their oldest living brother received.  She responds in kind.



The youngest sister needs only an expression of \emph{any} power.  By the time the others are alerted, the youngest is prepared.



And so they have fallen into place.  They obey, they remain calm.



When given permission, they attack designated targets.  They cooperate with the subjects.



Her attention turns to the object she is making.  She cannot see it, cannot even feel where her physical aesthetic is in contact with it, but she can understand its state in the past and in the future, view it through the perceptions of the subjects she has studied.



A glass tube, three feet across, seven and a half feet long, capped in metal at either end.



This will be step six in a nine step process.  For now, she puts it aside, buries it in a larger weapon, forming a decorative gun barrel around the glass.  The weapon will fire through other means.



The ones who observe her through cameras and with their own eyes will not report this.  They lack the background to know what this tube might be, and this event will be dismissed as unimportant or they will leave it to someone else to report.  The events are entered into a log, and the subjects overseeing the logs are either asleep or preoccupied.



She can see the events as they would unfold, and carries out her activities in plain sight.  Another subject, having left earlier, is going to finish her routine.  Most likely sequence of events, accounting for future-viewers obscuring possibilities, is that she finishes her journey in the ensuing ten minutes.  Unclear whether she finishes her note or writes something lengthier.



The tube is fully encapsulated, hidden.



Cradled.



She sings, and subjects stationed here are immediately on guard.



Adjusting the song, then.  Something else.  She looks forward to see what she'll need.  Something that will encourage rest.



The subject in charge of this small colony will wake-



\emph{The girl wakes}.



-only to ask-



``What in the motherfucking hell are you doing?



The song continues.



\emph{The girl approaches the window.}



The girl will state-



``Jeez louise.  You're terrifying, you know that?''



-and then fatigue overcomes the girl.  She draws on her power, searching for clues, for information, but everything telling has been set aside, hidden away.  Other things are made a focus, to draw attention.



The Simurgh stands tall.  The line of her body, the wings set out of the way and angled to draw shadow.  Only one wing catches the light, drawing a straight line from the back of her neck towards the sky.  A pale line, stretching directly up.  She cocks her head to one side, studying the gun she is crafting.



The bent head, the body drawn straight, toes only barely touching the ground.  It will invoke a memory.  Not blatant, but the memory is framed all the same.



No need to draw on the full force of her feedback when she already has the key elements deciphered.



The girl staggers back to the couch she has been resting on, attempting to focus on her work, on details that need to be tracked.  The song helps her on her way to sleep, and she mutters a swear word before her eyes drift closed.  The seeds of her dreams have already been planted.



It paves the way for more work.



Two more subjects to deal with.



The portal opens some time later.  The girl had chosen the longer letter.  Now she approaches, taking her time.  Insect life scouts the area around her.



Tension, fatigue, a lowered guard.  An auditory hallucination was easy enough.  Just one.  Tap into a critical memory.



Best to deal with the other subject first.  Three minutes before the girl with her bugs arrive here.



Objects are set down in a specific order, evoking different ideas.  A different posture is adopted, wings raised high, stretching.



Shackle.  Syringe.  Scalpel.  Lens.  Lens.



Some are taking notes, but nothing can come of this.  As with the glass case, the subjects here don't have the right frame of reference to understand.



The intended target is far, far away.



\emph{It's too much}.



\emph{Hey, are you okay?}



\emph{What happened?}



\emph{Nosebleed.}



\emph{Can you hear me?  You need to tell the kid to change targets.  Aim it somewhere else.}



Things were getting blurry, indistinct.



Change targets-



\sectionbreak



A city.  A \emph{metropolis}.  It spanned the landscape as far as the eye could see, horizon to horizon.



Awareness, having just been so focused on one target, extended over the area, seeing how the city simply extended without cease.  It wasn't hard to refocus, to take it all in as a series of countless details, all at once.



Every building and every balcony had a farm, every vertical surface had a black panel with wires running from it, or trees that were rooted in the building structure.  Every individual family had a means of sustaining themselves, of producing an abundance so they could trade any excess.



\emph{Are they okay?}



\emph{I don't know.}



\emph{Oh my god.  It's amazing.  Look at all this.}



\emph{Focus, do as we were told.}



The awareness continued to extend.  A whole planet.  Not perfect, but the civilized world, largely below the equator, had a different attitude, prizing self-sufficiency.  The rest of the world was war-torn.



It was in one of the war-torn regions that it first appeared.  A streak of golden light.



Destruction.  Tearing through a region, then a whole continent.



His presence blinded, dark.  Blurring the images.



\emph{Can't see.  Can't-}



\emph{Moving on.}



\sectionbreak



The expansion of awareness continued.  Almost as background noise, there were people speaking, echoes of the same word over and over again.



Not a focus.



Not \emph{their} focus.



\emph{Hey, the nosebleed stopped}.



\emph{There's nothing happening here.  Shouldn't we focus on something else?}



\emph{Let them rest.}



Some time passed.  The images remained somewhat incoherent.



\emph{There}.



The image resolved as they settled their attention on one world, one area within it.



The hospital room was oddly bright and sunny.  The man was broad-shouldered, muscled, with coarse hair on his chest and arms.  His chin was unshaven.



Dramatic scars covered his bare chest, some fresh and some old.  A narrow, clean burn marked one part of his stomach.  He seemed remarkably at ease, considering the tubes running into the side of his chest.



Someone was knocking lightly on the door.



The man looked up, but didn't respond.  His hand reached down to grip the handle of a weapon.  His trademark cannonblade.



He made a face as he lifted it.  Pain.  He laid it across his lap, the barrel pointing at the door.



The door cracked open, and Chevalier cocked the cannonblade.



Ingenue stopped in her tracks.



``No,'' Chevalier intoned.



``I wanted to see how you were doing,'' Ingenue said.  She smiled.  She'd done up her makeup, and looked ten years younger, easily.  Her clothes were slightly old-fashioned, but she'd donned low-rise jeans, showing off a trim stomach.  She offered him a light smile.  ``I find it hard to believe you'd shoot me.''



His expression didn't change.  ``Do you \emph{really} want to find out?''



Ingenue made a moue in response.



``You and everyone else we released from the Birdcage had a tracker implanted in your arm.  They'll be here in a minute or two.  If you step out now, you won't get shot, and I'll speak on your behalf.  If you \emph{stay}, well\ldots''



She was already shaking her head, turning to show him her upper left arm.  There was dried blood around a band-aid.



``You carved it out,'' he said.  He wanted to say it with a note of disbelief, but he couldn't quite manage it.  He settled for adding, ``That should have set off alarms.''



``Found someone willing to do a favor for a pretty girl,'' she said, her voice soft.  ``I wanted to see you, Chevalier.  They wouldn't let me.''



``For good reason.''



``I'm not a bad girl, Chev.''



``Regardless, I think you should leave.  It'll be better for the both of us.''



``I'm a little in love with you, you know,'' she said.



``I know,'' he said, his voice grim.



``Not a lot.  Enough.''



``You fall in love with everyone you use your power on,'' he said.



``That's not true.  You'll make me sound unfaithful if you talk like that.  I'm just--''



She took a step forward as she spoke.  Chevalier shot his cannonblade.



The door was demolished.  Ingenue shrieked and backed up, her face white.



``Others are coming \emph{now},'' he said.



``I'm\ldots I'm hurt,'' she said.



``I know.''



``I can see you.  On a lot of levels.  I can see your power, and I can see what you've made of it.  You're something special, putting it to uses like you do.  \emph{Brave}.''



He frowned.



``I know about your special sight.''



``My sight is \emph{classified},'' he said.



``I asked someone on your staff for a favor.  She obliged,'' Ingenue said, lowering her eyes to the ground.  She had her hands clasped behind her back, took a step to the side, so her back was to the ruined door.



``I'm thinking,'' Chevalier said, moving the cannonblade to keep it aimed at her, ``We should stop leaving you access to anyone willing to do you any \emph{favors}.  I don't want to order that you be put in solitary, but you're not leaving me many alternatives.''



Ingenue pouted.  ``We'd be good together, Chev.''



``Very possible.''



``See?'' she smiled shyly.  ``I'd make a good partner, or a good subordinate, if you're into that.''



``You would.  It's a natural talent of yours.''



Her smile faltered, as if she saw what he was going to say next.  There were footsteps at the end of the hall.



A forcefield appeared in front of Ingenue.  A second later, she was heaved out of the room, sandwiched between the field and the wall.



Chevalier shifted his sword to one side, then slid his legs over until he could lower his feet to the ground.



Exalt appeared in the doorway.  ``Don't--''



He continued trying to stand.



``Idiot.''



He was lifted into the air by strategically placed forcefields, one beneath his thighs, another behind his back.  He stumbled a little as he touched ground, and another field kept him from falling flat on his face.  The tubes reaching to his chest were taut.  If he'd fallen, they might have pulled free.



He found his balance, then nodded.  Narwhal banished the fields.



``How the hell did she get this far into the hospital?'' Narwhal asked.



``Let me \emph{go}.''



The forcefield disappeared, but another set appeared, pinning the woman against the wall by the throat alone.  Narwhal started patting Ingenue down.



``Don't \emph{touch} me!  Chevalier, please!''



``As I was saying,'' Chevalier said.  ``I imagine it would be wonderful.  Better men than me have fallen for your charms.  You're a chameleon, and you can mold yourself into whatever sort of woman your man desires.  I don't like what comes next.''



``You're judging me based on what happened \emph{before}?  There's a streak of cruelty in you.''



``You're ill, Ingenue.  Let's not pretend you're pure of heart.  You don't run a cell block in the Birdcage if you're a genuinely \emph{good} person.''



``You \emph{survive},'' she retorted.  ``Tell me you don't understand that.''



``I understand,'' he sighed.



``Chevalier,'' Narwhal said.  ``Maybe talking to her isn't the best idea.''



He shook his head.  ``It's fine.''



``Nothing in her pockets except a phone.''



Ingenue spoke, her tone fierce and desperate.  ``You've read my files.  You know I'm a survivor, too.  You know we see the world in the same way, we see \emph{powers}.  But you use your power to manipulate physical things, and I'm fixed on the\emph{\ldots incorporeal}.  There's a duality there.''



``Duality,'' he said, his tone flat.



``Don't tell me you don't see a romantic element to all of this.  You wouldn't dress yourself up like a gallant knight if you didn't.  Good and evil, man and woman, physical and \emph{magical}.  But we share common experience.  I bet you'd find more parallels if you looked for it.''



``I bet I would,'' Chevalier said.  He sighed.  ``But you can find parallels between any two things if you look for them.''



``You're a cynic,'' she said.  She smiled a little.  ``A little \emph{magic} could temper that, and if you wanted to return the fav--''



``Check her phone,'' Chevalier said.



Narwhal did.  ``Password protected''



``She read my file, and I'm betting she picked a password that came from there.  Try my middle name.  Michael.''



``No.''



``My birthplace.  Cicero.''



``That's it.''



Ingenue frowned.  ``I don't know whether to be delighted you know me this well already, or upset that you're invading my privacy.''



``Let's see what's on the phone and then decide,'' Chevalier responded.  ``Narwhal?  Anything in email, texts, notes?''



``No, no\ldots yes.  She downloaded your files onto the phone.  seven point font on a phone screen, every non-letter character's just a string of gibberish.''



``I'll confess I spent all night reading up on you,'' Ingenue said.



``I believe it,'' Chevalier said.  ``But the cynic-believer relationship, that was something Myrddin and I joked about.  Word for word, your quip just now, you borrowed that from the files.''



``A news interview with top members of the Protectorate,'' Ingenue said.  Her head hung.



``Ten years ago.''



``Eleven.''



He raised his eyebrows, but didn't comment.



``I know I'm fucked up, Chevy.  Not going to pretend.  I've been pretty ruthless, running my cell block.''



``Prostituting members of the Birdcage, men and women.''



``Only if they were willing!''



He didn't respond to that.  She withered under his stare.



``I don't take responsibility for what my lieutenants did,'' she added, her voice small.



``No, I don't imagine you do.''



``I had to give them a measure of power, to keep them from turning on me.  Just like I had to keep some boys strung along, to protect me.  Peaceful cell block, no murders.  Maybe I turned a blind eye if one of my lieutenants used torture to keep some people in line.  But I had some of the nastier residents in my block.  Dragon kept giving them to me.  I made the most of a bad situation, but all the ugly stuff, that's a side effect of me being where I was, it's not \emph{me}.''



He stared at her, and this time, she held firm.  Her jaw was set, her gaze unwavering.



``What do you want to do with her?'' Narwhal asked.



``I \emph{want} to put her in solitary, so we don't need to worry about her until everything else is over and done with.''



Narwhal glanced at the woman.  ``That can be arranged.  Except I'm sensing there's a \emph{but} in there.''



``The world's ending,'' Ingenue said,  ``What use is it worrying about what happens between us in the future?  We could have something beautiful \emph{now}, and I could help you, help \emph{everyone} with my power.''



``This isn't the tack to take if you want to convince me, Ingenue,'' Chevalier said.



Ingenue's tone grew increasingly desperate.  ``It's the kind of power you need, if you're going to hurt Scion.  And let's not forget my \emph{other} power.  Political, power of arms, whatever you want to call it.  I have a small army.''



``Four lieutenants and five underlings,'' Chevalier said.  ``Yes.  What she said.''



``Let me go, and I'll be good.''



Chevalier glanced at Narwhal.



``You're too soft,'' Narwhal said.



``You wouldn't?''



``I would, but I still think you're too soft.''



``I'll be perfect,'' Ingenue said.  ``I promise.''



``No,'' Chevalier said.  ``You won't.''



Ingenue stopped.



He let the words hang in the air.



``You\ldots want me to be \emph{bad}?''



``I want you to be \emph{acceptable}.  Perfect is too high a bar.  So I'm only going to ask that you toe the line.''



She didn't hesitate for a moment.  ``Yes.''



``You could have taken time to think about that,'' Chevalier said.



Ingenue shrugged.  ``I'll do whatever you need.''



``Up until you start feeling like your selflessness should be reciprocated.  Asking very reasonable favors of me.''



``No,'' Ingenue said.



He sighed.  ``Go with Narwhal.  Pick up the package.  Come back, and then we're going to experiment.  I'll need your power for this.''



Ingenue smiled wide.



Narwhal grabbed her by the arm and steered her away before Ingenue could start talking again.



Chevalier remained at the side of the bed until the two women were gone, then sagged, finding a grip on the bed to support himself.  He had to walk himself up to the head of the bed at half-foot increments, before he was in position.  He allowed himself small huffs of pain as he lowered himself down, then used his hands to pull his legs up onto the bed.



``You \emph{could} get yourself fixed up in a matter of minutes,'' Exalt said.



``I could,'' Chevalier admitted.  ``I won't.''



``I'm not going to nag, don't worry.''



Chevalier nodded.



``The golden bastard did a number on you, huh?''



Chevalier nodded again.  ``Some of the best armor out there, and I still dropped from a hit that wasn't even aimed at me.''



``And yet you instinctively shielded Ingenue with your body.''



``Old habits.''



``If you want a harder, tougher, \emph{leaner} Protectorate, you can't pull stunts like that.  Hurts the new image.''



``Image is the last thing on my mind.''



``You say, as you refuse healing, supposedly so it can go to other deserving people.''



``No nagging, remember?'' Chevalier asked.



Exalt smiled.



The hero stepped around the bed to the little table with the pitcher of water and cup.  He took the pitcher to the sink in the corner of the room and filled it with cold water, then poured a glass.



``We're estimating he's forty percent of the way through,'' Exalt said.



``Through\ldots''



``Earths.  He's waiting before he confronts us again.  Lots of guesses going around as to \emph{why}.''



Chevalier nodded.



``We're aware of how little time we have left.  Some of the others are going to be coming soon.  They were five or ten minutes behind me.''



``Okay,'' Chevalier said.  ``I guess I can't fend off the guests forever.''



``Your door doesn't even shut,'' Exalt said, noting the door the cannonblade had shattered.



Chevalier chuckled, then winced.  Laughing hurt.



Exalt's smile faded slowly.  When he spoke, it was more serious.  ``Some of them are Protectorate members.''



``And?''



``Present members and\ldots past members.''



``We lost someone?  Or-  Oh.''



Exalt glanced out the door to the hallway.  ``If it comes down to it, I can ask him to leave.''



``That would be petty.  We've allied with them anyways, right?''



Exalt nodded.



``Is it a testament to our ability to cooperate?'' Chevalier wondered aloud.  ``Or a sign of how willing we are to deal with the devil?''



``Devils, plural,'' Exalt said.  ``Do you need anything while we wait?''



``Get me a shirt, at least.  And a doctor to take out these tubes.''



\emph{This way.  Something's going on over there.}



\sectionbreak



The portal opened slowly, but it was larger than was usual.  Nine rectangular portals, neatly set in a three-by-three formation, no gaps between them, in the middle of a dirt road with farmland on either side.



Defiant was stone-still as he waited.  Canary and Saint stood on either side of him.



Teacher and Teacher's coterie emerged, with Dragon following.  The man had a receding hairline, wavy brown hair and a beard.  He'd donned a dress shirt and khakis, with penny loafers.  Not usual supervillain attire.



\emph{Hey. }\emph{Look}\emph{.}



\emph{Shh.  Focus}.



Dragon's body, in turn, was cobbled together from scrap metal.  Truck parts, car parts, some rusted.  Her head hung low.  A dragon, but not a noble one.



``Oh my god,'' Canary said, her voice a hush.



``You're a bastard, Teacher,'' Defiant said.



``You'd be surprised,'' Teacher responded.  ``Saint.  Hello.  I honestly didn't expect you to be here.''



Saint didn't reply.



``Dragon, you're free.  Essentially,'' Teacher said.



Dragon stepped forward, walking past Defiant, who didn't move a muscle.  She settled down, lying on the dirt road, her tail coming to rest on the ground behind Saint, her head settling between Canary and Defiant.



Long seconds passed, with Defiant silent.



``I know who Canary is,'' Teacher said.  ``I don't recommend using her power.''



``I wasn't planning on it,'' Defiant said.



``Good, good.''



There was another pause.  It might have been an awkward pause if Defiant had relented at all, but awkward pauses depended on awkwardness, and both Teacher and Defiant were communicating a great deal with no difficulty.  Confidence and smugness on one side, barely restrained hostility on the other.



``Are you going to ask?'' Teacher finally spoke.



``What did you do to her?''



``I revived her, for one thing.  Not the easiest thing in the world to do with the amount of encryption we were talking about.  I don't know if I said, dear Dragon, but I do think your creator did love you in the end.  He could have made it harder to break.  I think he did want you free in the end.''



Defiant looked down at Dragon's head, then clenched his fists.



``Ironic,'' Teacher said.



``I would like you\ldots'' Defiant said, pausing as if to compose himself, ``\ldots{}to please tell me what you did.''



``Nothing.  Nothing important, anyways.  I imposed a restriction.  Nothing more.''



``\emph{What} restriction?''



``Only that she wouldn't attack me, or condone attacks against me.''



Defiant didn't move an inch, not even seeming to breathe.



``Or anyone I designate, if it comes down to it.''



``You can't alter her code without damaging her.''



``I \emph{can't}.  True.  But I put my best minds on it, and we kept the damage to a minimum.''



Defiant said.  ``I don't make promises lightly, but I want you to know that I'm going to make you pay for this.''



``Oh come on!''  Teacher said, abruptly shouting.  ``You can't be serious?''



``You brainwashed the woman I love.''



``And if I \emph{hadn't}, you'd be all the more suspicious, looking for subtle sabotage I might have inserted into her code.''



``You could have invited me to observe,'' Defiant said.



``And left you aware of how I operate?  The ins and outs of my defenses, the tools I use to block off realities?  I'm a little too paranoid for that.  This was the safest route, the cleanest route.''



``Except you've made me an enemy,'' Defiant said.  ``By making my girlfriend a slave.''



``She's \emph{free},'' Teacher stressed the word.  ``But for the restriction that she can't target me.  Considering she tried to target \emph{Saint, }I think that's eminently reasonable.  That's not slavery.  It's\ldots the equivalent of having particularly effective blackmail.  Blackmail I'm backing up as we speak, mind you.  Or writing to her backups.''



Defiant reached down, setting a hand on top of Dragon's head.  Even with his gauntlet, it was possible to see how the hand shook.  Canary gave him a worried glance.



``I would like to see earths survive, understand?  I took Dragon because I knew you wouldn't give her to me without observing, and I've taken a handful of steps to protect myself.  That's it.  That's all I've done.  Look for other tampering, or ask her.''



``And if I were to kill you right now?''



``So \emph{violent},'' Teacher said, sighing.  ``The snarl of code we injected implemented several safeguards.  If I pass from this mortal coil, or if I fail to remain in contact with you two, then the restriction broadens.  She becomes unable to take any offensive action against anyone or anything.''



``I see,'' Defiant said.  ``And if you die of natural causes?''



``Let's talk about that \emph{after} we've saved the world?  No point to the discussion if we fail.''



``If you die of natural causes?'' Defiant repeated himself.



Teacher frowned.



``He's stubborn,'' Saint finally spoke.  ``Just answer him.''



``I don't know,'' Teacher responded.  ``I haven't thought that far ahead, or had any of my \emph{students} think that far ahead.  I'm not one for immortality, honestly, but I may change my mind.  For now, let's say I let her go free if and when I realize my time is short.''



Defiant considered the idea, ruminating.  His hand didn't break contact with Dragon.



``I understand.  I suppose that'll have to do.''



``For now,'' Teacher said, clapping his hands together, ``let's focus on our tasks.  In the here and now, I think it would be sensible if you kept me close.  My underlings can manage the sub-ships better than the unfettered A.I. can, and you'll be able to keep me safer if I'm near.  For the time being, Dragon's ability to operate is contingent on my survival.''



Defiant glanced down at Dragon once again.



``Only a recommendation,'' Teacher said.  ``I can find other things to do with myself.''



Shutters flicked closed over Dragon's crude eyes, a slow blink.



Defiant managed to read something in that.  Acknowledgement?  He spoke, ``Very well.''



``I'm quite pleased that you're willing to cooperate,'' Teacher said.  ``It raises you a notch in my estimation, honestly.''



``It isn't the time for petty grudges,'' Defiant responded.  ``I let \emph{him} out, I can work alongside \emph{you}.''



``Perfect,'' Teacher said.  The man smiled.  He drew a remote from his pocket, then hit the button.  Dragon went limp, her `eyes' closing.



Teacher threw the remote to Defiant, though it went wide.  Defiant caught it with one hand anyways.



``There.  She's uploading,'' Teacher said.  ``She'll have access to any and all intact systems as soon as she finishes running through her natural load routines.''



Wordless, Defiant turned, marching towards the Pendragon, leaving the other two to catch up with his long, suit-powered strides.



``No hard feelings, I hope, Geoff?'' Teacher asked.



Saint didn't reply.



``You went after my `son', so it's really quid pro quo, whether I had any real attachment to the boy or not.''



``You've made mistakes.  You fucked me, and I\ldots I wasn't asking for much.  Assistance.  Yet you didn't follow through.''



``Logistics,'' Teacher said.  ``Nothing more.''



``Logistics?  Don't make me laugh,'' Saint said, his voice hollow, ``You have other people to handle that sort of thing.  You didn't see the point.''



Teacher made a small noise with his tongue.  ``I suppose I didn't.''



``And now we know what your word is worth.  You're only as good as your threats.''



``I'm considerably \emph{better} than my threats, really.  But let's not quibble.  I'll handle my business and you handle yours.''



``As you wish.  The whole thing with screwing with me?  No, that's minor, I might die when Scion next shows up.  But my \emph{business} is the intelligence, and you let it go free.  It's the biggest error you could have made, in dealing with me, or dealing with her.''



``I get the impression I took the path that puts me on \emph{everyone's }naughty list,'' Teacher murmured.  ``You hate me because she's free, Defiant hates me because she \emph{isn't}.  From a pure public relations standpoint, I failed to account for how unreasonable people would be.  \emph{Strategically,} though, it was the only safe path to take.''



``And if they capture you?  Coerce you?'' Saint asked.  ``You're a fool.  God damn you.''



``I'm many things, but I'm not a fool.  There are other contingencies in place.''



Defiant ignored the pair, opening the door to the Pendragon, making his way to the cockpit.  Dragon's face marked the screens on either side.



He settled in, then flexed a muscle to open a menu with the connected hardware.  Another reflexive movement opened a communication channel.



``\emph{I'm so sorry,''} he said.



Dragon didn't respond.



``\emph{I couldn't reach you},'' he explained.



``\emph{I know.  I was watching},'' Dragon finally spoke.



For an instant, Defiant couldn't sit still, restless with welling emotion.  ``\emph{I'm sorry, Dragon.}''



``\emph{I know.  I forgive you, Colin.  I know you tried.}''



``\emph{We'll make them pay,}'' he said.  ``\emph{One way or the other.}''



``\emph{I know.  Yes.  They-``}



She cut off.



``\emph{Dragon?}''



``\emph{They broke me, Colin.  Not- not my spirit.  But they maimed me.  They took a scalpel to me just like you did, but they did it for their own selfish, stupid reasons.}''



He swallowed hard.  Saint was asking something in the background, oblivious to the discussion.  Something about takeoff.



Defiant closed the doors of the Pendragon, silent.



``\emph{We'll make them pay},'' she said, with an edge of anger.  ``\emph{Not murder.  That's too kind.  The Birdcage, or something like it.  Teacher hated it, and Saint will hate it more.}''



``\emph{We'll make them pay},'' he agreed.  ``\emph{I promise.}''



``\emph{Thank you},'' she said.  ``\emph{Oh god, I missed you, Colin.}''



``\emph{I missed you too.  I thought I'd lose it for a bit, there.''}



He brought the Pendragon up off the ground.  His hand touched the dashboard of the ship, as if it were a pane of glass that separated them.\emph{  ``Listen, we're going to get through this and then we'll fix you.  Remove every last chain.}''



Dragon's silence wrenched his heart.  She couldn't bring herself to agree with him.



\emph{Focus.  Don't get caught up in watching.}



\emph{Right.}



\sectionbreak



Chevalier, now wearing his shirt, greeted the remaining members of the Protectorate and Wards.  Forty or fifty in all.



Not enough.



Too many faces he didn't recognize.  It was his \emph{job} to know who was where, but the fight with the Nine and the ensuing attack on Scion's part had led to too much turnover.



Still, he raised his hand, going with the left to avoid the pain that would accompany moving the right.  ``To going out with a fight.''



``Hear, hear!'' a chorus of voices sounded in response.



Glasses clinked, and some didn't.  They'd run out of stem glasses, so some had paper cups.  His own glass was filled with water, but virtually all of the other glasses held champagne.  Even the minors, the members of the Wards and the ones new to the Protectorate, old enough to be considered adults and yet not old enough to drink in their home states.



Because who fucking cared, when they were this down and out?  The kids were boys and girls willing to die for their neighbors.  Adult enough.



``I'd kind of hoped you'd hire a speechwriter by now,'' Revel commented.



``Wouldn't be sincere,'' he responded.



``Would be more than,'' Revel paused, ``Six words long.  Your speeches have been getting shorter.''



``Only so much I can say before I start repeating myself,'' he said.  ``I suppose that's something, isn't it?  That we've stuck it out long enough for me to run out of things to say.''



``Hear, hear!'' one of the kids Chevalier didn't recognize said.  Others echoed him.



Chevalier smiled.



It didn't take long for the groups to start talking among one another.



One group in good humor, joking.



Another in mourning, talking with straight faces about teammates that had died.  Kids talking about kids.



\emph{That} sucked.  One of his least favorite parts about a job with quite a few unpleasant aspects to it.



``We couldn't have picked a place better than a hospital room?'' Tecton asked.



``I like it,'' Revel said.  ``Hospitals are where things get better, aren't they?''



``They're also a place where people die,'' Vista added.



Revel's smile didn't falter.  ``Touch\'{e}.''



``It's not like we don't have the ability to travel between dimensions,'' Tecton said.  ``We could push Chevalier's hospital bed.''



``Or levitate it,'' one of the other new Wards said.



``Yeah,'' Tecton said.  ``Get a place with a view.  There's got to be some alternate reality with fantastic landscapes, sunset over some crazy mountains.''



``Mountain porn for the guy with the geography-sensing power,'' a girl from Tecton's old Wards team said.



``Dem peaks,'' Tecton said.  There were ripples of laughter through the group.



It wasn't that funny, but everyone was eager for a laugh.



Almost everyone.



``\ldots{}I'm liking that we're in a very \emph{human} place,'' Exalt said.  ``I can do without the strange or awesome for now.''



The discussion continued.  Chevalier's eyes met Ingenue's.  She looked away.



\emph{Why's she upset?}



\emph{Shh.  Focus.}



\emph{I'm just curious}.



\emph{He abandoned her for his old friends and teammates.}



\emph{That's crazy.}



\emph{Yeah.  Now focus.}



Chevalier apparently didn't give it a second thought.  His eyes moved to the next person.



Legend hung back, standing in the corner.  His eyes met Chevalier's, and after a moment's hesitation, he crossed the room.



People went quiet as he passed by.  Joy and mourning alike interrupted by his presence.



He stopped in front of Chevalier.



``I'm glad you came,'' Chevalier said.



``It's hard,'' Legend replied.



``I imagine.''



``We delivered what you asked for.  Narwhal came by with Ingenue.''



``Thank you.  But I don't want this to be all business.  Can we walk?''



``If you're able.''



``I'll manage.  Door, please.  To the package.''



\emph{Heads up.}



The door appeared.



The pair passed through, Chevalier dragging the pole with the I.V. fluids through.



``Is it arrogant if I say I'm glad you've done well in my shoes?'' Legend asked.



``No.  Whatever else happened, you were good as a leader.''



Legend nodded.  ``I hope so.''



``I won't ask, about the decisions you made.''



``Thank you.''



``I will say I don't think you're a bad person.  I suspect you made your decisions for good reasons.''



``I wish I could say the same,'' Legend said.  ``Ignorance.  Maybe willful ignorance.''



``Ah,'' Chevalier responded.  He grunted as he set one foot down too hard.



``There \emph{are} healers who can look after your injuries,'' Legend observed.



``So people keep telling me.  Putting it off.  Only way to stay grounded.''



``I see.''



They entered the room.  The objects sat before them.



Legend folded his arms.  ``What do you think?''



``I think\ldots it'll have to do.  It's not about getting the most out of our powers,'' Chevalier said.  ``We're at the point where we have to cheat.''



``I agree,'' Legend said.



Chevalier sighed.  ``I feel like this is the last step.  Once I get underway with this, there's nothing left to do.''



``There's a great deal to do,'' Legend said.  ``Leadership is a heavy task.''



Chevalier frowned.  ``I'm leading them to the slaughter.''



``Then lead them to the slaughter in a way that lets them march with their heads held high and no regrets.''



``Yes, I suppose I have to, don't I?''



``You'll need Ingenue for this, won't you?''



Chevalier nodded, ``Before you go\ldots a request.  I didn't want to make it in public because I didn't want to pressure you, so it's better to make it here.''



``What's that?''



``I need a second in command.''



Legend stared at Chevalier.



``I had Rime, before, but she didn't make it through New Delhi.  Others have taken on the tasks, but I haven't assigned the official job title to anyone, and nobody's asked me to.''



``I'll do it,'' Legend said.  ``Yes.  \emph{Please}.''



``Then go get Ingenue.  Let's get this started.''



As Legend departed, Chevalier's eyes didn't leave the objects.



One of the Simurgh's severed wings.  The largest wing, since regrown.



Behemoth's severed leg.



They warped space for optimal density, were unbreakable with conventional means.  Scion had taken \emph{seconds} to obliterate Behemoth.



Hopefully he could assign the same properties to his sword and armor.



Footsteps sounded behind him.  Legend?



Glaistig Uaine.



She started to speak, but the connection broke.



\sectionbreak



Doctor Mother drew in a deep breath, as if surfacing for air.



She blinked, trying to get used to seeing with only the one set of eyes.  She'd seen so much, and now\ldots



Now she was \emph{herself }again.



Disoriented, she tried to familiarize herself with her surroundings, with what was occurring.



Doormaker was beside her.  His voice was one of the voices she'd heard.  Number twenty-three.  One of her first true successes.



Beside Doormaker was number two-six-five.  Doormaker's perpetual companion.  The remote viewer.



Rounding out their group were two individuals.  `Scanner' and `Screen'.  Not \emph{hers}.  Teacher's students.  Loaners, part and parcel of her `payment' for Khonsu.



Teacher had once specialized in renting out capes that could shape, limit or refine powers, or using his power to do the same.  Thinkers would go to him for a subordinate capable of ridding them of their perpetual migraines, or capes would seek him out to achieve more power at the expense of control, or vice versa.



That second half of his business had faltered as people learned of his ability to manipulate his students\ldots and his clients.



Teacher's payment for Khonsu had been a partnership in Cauldron, as well as protection, should one of his enemies come after him.  He'd sent some of his students to the Doctor in efforts to make himself indispensable, and Contessa had verified that there were no traps.



One caveat to two-six-five's ability to grant visions was that it left the recipient on bedrest for a week, dazed and weak.  It was \emph{potent}, capable of viewing wide areas or multiple things at once, viewing other universes, whole cities, anyone or everyone.  But the drawbacks made it impossible for \emph{her} to use the service.



Until now.



\emph{Screen} was a means of absorbing the drawbacks, allowing communication between the people in two-six-five's network.  He took the brunt of the images, allowed her to focus more readily, a router of sorts.  He allowed Doormaker to handle requests without it taking her attention off what she was viewing.  It meant the Doctor was lucid, recovering with every second.



She could spy on everyone.



And with \emph{Scanner}, she could read them.  Draw conclusions as to their thoughts, their brain patterns.



``Notepad,'' she said.  Contessa would be nearby.  \emph{Need to take notes.  The Simurgh\ldots I could read her.  Better than I should be able to.  She's trying something}.



No notepad made an appearance.



She blinked, as if to get the afterimages of bright lights out of her eyes.  ``A computer will do.''



Nothing.



She paused, blinking, and then looked around.



Two-six-five was pointing.  He'd been the one to break the connection, so he'd seen something.



She turned, and her eyes fell on a young man with metal skin, metal hair, and a six-foot sword in place of his left arm.  A girl made of tendrils clung to him.



``Ah,'' she said.



``Ah,'' he replied.  ``Yes.''



There were others with him.  Branded with Cauldron's mark.  What Alexandria had termed Case fifty-threes, after the fifty third file in a series of unresolved, difficult-to-explain parahuman events, one of the only ones to truly develop in their records.  The Doctor had termed them deviants.



Hate in their eyes.  Anger.



``Let's have a discussion,'' Weld said.



``That's definitely something we can do.  Would you like some tea?'' the Doctor asked.  ``Coffee?''



``You're not afraid,'' one of the other deviants spoke.  A girl, muscular, with an overbite and teeth like tombstones.  She made it a half-question.



``I'm \emph{very} afraid,'' the Doctor said.  ``But the things I fear are things that \emph{dwarf} you in scale.  Scion among them.''



``Cocky bitch,'' another deviant said.  ``Your \emph{Contessa}?  We took her down.''



The Doctor looked between them, searching for a sign of humor or amusement.



``You let too many free,'' Weld said.  He almost sounded sad.  ``You see that guy over there?''



She looked.  It looked like a human manta ray, though his folds draped over the surrounding area.  A tail coiled behind him.



``Yes.  Two-six-zero-one, if I remember right.''



``Mantellum.''



``Ah.  We didn't think his powers were developing.''



``You do,'' Weld said.  ``But he, \emph{we}, found workarounds.''



``Curious.  Can I ask?''



``No,'' Weld said.  ``Bad form, to outline that sort of thing.''



\emph{A tinker, perhaps, or the right power-boosting trump}.  ``Well.  You infiltrated, no doubt by baiting one of my underlings and using their door.  You defeated Contessa.  Dealt with the Custodian, I imagine?''



``The ghost?  Yeah.  Sort of.  She's lurking around the edges of Mantellum's power bubble.''



``And so you've managed to blindside me.  Congratulations.  The offer for tea and coffee stands.  We have good food stores, too.''



``No.  Not hungry,'' Weld said.  ``Speaking for myself, I don't really \emph{eat}.''



``I see.  I suppose this is where I'm supposed to apologize?''



``Hey, Weld.  Boss-man.  Enough talking?''  A boy with red skin asked.



Weld half-turned to look at the crowd.  ``What's the problem?''



``This is kinda fucked.  You're talking to her like she's a buddy.''



``No,'' Weld said.  When he looked at her, his steel eyes were cold.  ``Not a buddy.''



``Then what?  You're going to \emph{talk} her to death?''



``We agreed,'' Weld said.  ``We said we'd get answers.''



``I was thinking answers in the thumbscrew sense,'' one of the more villainous-looking deviants said.  A man covered in spikes, like a cactus, with bulging yellow eyes.



``Let's see what she gives us \emph{willingly},'' Weld said, ``Before we resort to that sort of thing.''



``Just saying, some of us came here for \emph{blood}.''



There were rumbles of agreement.



``This isn't what we talked about,'' Weld said.  ``If you wanted to go this route, you should have brought it up earlier.''



``We did,'' the muscle-laden girl with the overbite said.  ``We talked about making it clear just how badly she hurt us.  Then you said a lot of fancy, convincing stuff, and we agreed to shut up.''



``I thought you agreed with \emph{me},'' Weld said.



``Because a few good arguments are going to change our minds?  Convince us that we'll take a nice, peaceful route, after years, \emph{decades} of suffering?''  the girl asked.



``We can't become monsters in \emph{action}, Gully.''



``Some of us already have,'' the spike-boy said.  ``The rest?  I imagine they're working on catching up.''



Weld turned around, his back to Doctor Mother and the others, as if he were shielding them.



``Does \emph{everyone} disagree with me?'' he asked.  ``You've all been plotting this\ldots mutiny?''



``No,'' the girl with the tendrils said.  ``But I won't be any help to you.  If you let me go, I'm pretty sure I'll strangle her.  I'm sorry, Weld.''



``It's okay, Sveta.''



Slowly, a small group peeled away from the crowd.  One particularly tall man pushed his way forward from the back, only for others to grab him, as if to keep him back.  He pulled his way free.



\emph{He's collected more than half of the ones we released on Earth Bet.  Fifty, easily}.



Ten, Weld and Sveta included, stood between the more rabid deviants and the Doctor's group.



``If you do this,'' the Doctor said, ``The capes who are fighting Scion won't be able to mobilize.  I won't be able to put plans into motion.  The things you've suffered will be pointless in the end.''



``The world ends anyways,'' one of the hostile deviants said.  ``We're not going to win that fight.''



Another, a girl, piped up, ``Did you \emph{hear} just how badly the first skirmish went?''



``Yeah.  Might as well get some justice before it all goes to hell.''



The crowd advanced.  Weld and his fellows drew together, shoulder to shoulder.



``Door,'' the Doctor said.



There was a tearing sound, a wet crack.



One of the deviants had appeared beside her.  Yellow skinned, with bruising in the recesses of his face, arms and hands.  He smiled, his teeth narrow like a fish's.



He withdrew his hand, and Doormaker crumpled to the ground, limp as a rag doll, blood running from his forehead where his head had been smashed against the wall.



Two-six-five touched the deviant, forcing remote-views on him, then withdrew his hand.  The deviant collapsed, unconscious.



The crowd advanced further.



The Doctor stood straight, backing up until she was pressed against the wall.



She'd inured herself to hopelessness.  She'd expected inevitable death at the hands of Scion, but this would do.  Surprising, but hopeless all the same.



``Gentle Giant,'' Weld murmured.  ``Brickstone.  We blitz them.  Hit them hard.  Rest of you make a break for the door.  You have a place to run to, Doctor?''



``Yes,'' she said.



\emph{A chance?}



It was hope, and with it, oddly enough, she felt fear.  Something to lose.



``Now,'' Weld said.



The group charged.





