





``You actually showed up.''



I looked up from my math textbook to see Emma looming over me.  She was wearing an expensive dress that had probably been a gift to her after one of her modeling contracts, and her red hair was up in the kind of complex knot that looked ridiculous on ninety-five percent of the girls that tried to pull it off.  She could make it work, though.  Emma was one of those people who just seemed to ignore the social awkwardness and minor issues that plagued everyone else.  She didn't get zits, any style she wore her hair or clothes in looked good on her, and she could break pretty much any social code of high school and walk away unscathed.



God, I hated her.



Mr. Quinlan had ended class fifteen minutes early and instructed us to do some self study, before leaving the room.  For most, that was a chance to play cards or talk.  I'd set myself the task of getting all the homework done before class ended, to free up my weekend.  At least, that had been the plan, before Emma interrupted.



``Funny thing is,'' I replied, turning my attention back to my notebook, ``You're the only person today who seemed to notice I was gone.  If you aren't careful, I might actually think you cared.''  I wasn't being entirely honest there.  My art teacher had noted my absence, but that was only after I'd reminded her I hadn't turned in my midterm project.



``People didn't notice you were gone is because you're a nobody.  The only reason I paid any attention to it is because you bother me.''



``\emph{I }bother \emph{you},'' I looked up from my work again, ``\emph{Wow}.''



``Every time I see you, it's this irritating little reminder of time I wasted being your friend.  You know those embarrassing events in your past that make you cringe when you think back on them?  For me, that's basically every sleepover, every juvenile conversation, every immature game you dragged me into.''



I smiled, then against my better judgement, I told her, ``Right.  I love how you're implying you're even remotely more mature than you were then.''



Strange as it sounds, I was actually relieved to have Emma here, getting on my case.  If this was all she was able to do to me today, it meant I probably wouldn't have to deal with any `pranks' in the immediate future.  What really ratcheted up the anxiety levels was when she ignored me and left me alone.  That was, generally speaking, the calm before the storm.



``Really, Taylor?  Tell me, what are you doing with yourself?  You're not going to school, you have no friends, I doubt you're working.  Are you really in a position to call \emph{me} immature, when I've got all that going for me and you just\ldots don't?''



I laughed loud enough that heads around the classroom turned in my direction.  Emma just blinked, bewildered.  As much as I didn't want the money,  I was technically twenty five thousand dollars richer than I had been thirty six hours ago.  Twenty five thousand dollars were waiting for me, and Emma was saying she was doing better than me, because she got a few hundred dollars every few weeks to have her picture taken for mall catalogs.



``Fuck you, Emma.''  I said it loud enough for others to hear.  ``Get a clue before you try to insult people.''



With that said, I grabbed my stuff and strode out of the classroom.



I knew I was going to pay for that.  For standing up to Emma, for laughing in her face.  It was the sort of thing that would push her to get creative and think about how best to get revenge for that small measure of defiance.



I wasn't that worried about skipping out of class five minutes early.  If history was any precedent, Mr. Quinlan probably wouldn't be coming back before class ended.  He routinely left class and just didn't come back.  Popular guesses among my classmates leaned towards Alzheimers, or even that our geriatric teacher with a sagging gut could be a cape.  I was more inclined to suspect that drugs or a drinking problem were at play.



I felt good.  Better than I'd felt for a long, long while.  Admittedly, there were painful stabs of conscience when I thought too much about the fact that I'd actually participated in a felony, or the way I'd terrorized the hostages.  Could I be blamed if I went out of my way not to dwell on it?



I'd slept like a baby last night, more due to sheer exhaustion than sound conscience, and I woke up to a day that kept surprising me with good news.



Brian had met me on my morning run, and he treated me to coffee and the best muffins I had ever tasted, while we sat on the beach.  Together, we had taken ten minutes to go over the morning papers for news about the robbery.



We hadn't made the front page for any of the major papers, the first bit of good news.  We made page three of the Bulletin, coming behind a one and a half page story on an Amber Alert and a General Motors advertisement.  Part of the reason we hadn't attracted all that much attention was probably because the bank was hedging about the amount taken.  While we had escaped with more than forty thousand dollars, the paper was reporting losses of only twelve.  All in all, the story had been more focused on the property damage, most of which was caused by Glory Girl and the Wards, and the fact that the darkness we'd used to cover our escape had stopped all traffic downtown for an hour.  I'd been quietly elated by all of that.  Anything that downplayed the magnitude of the crime I'd helped commit was a good point in my book.



The next mood booster was the fact that I'd gone to school.  It sounded dumb, rating that as an accomplishment when others did it every day, but I had been very close to just not going again.  Having skipped a week of afternoon classes and three days of morning classes, it was dangerously easy to convince myself to just skip one more.  The problem was, that just made the prospect of going to class again that much more stressful, perpetuating the problem.  I'd broken that pattern, and I felt damn good about it.



Okay, so I had to admit things weren't a hundred percent perfect as far as school went.  I'd talked to my art teacher, and she was giving me until Tuesday to hand my midterm project in, with a 10% deduction to my mark.  I'd also probably lost a few marks in various classes for being absent or not handing in homework assignments.  One or two percent, here and there.



But all in all?  It was a huge relief.  I felt good.



I caught the bus to the Docks, but I didn't head to the loft.  I made my way up the length of the Boardwalk, until the shops began thinning out and there were longer stretches of beach.  The usual route people took was driving in through a side road outside of town, but for anyone hiking there, you had to take a shortcut through a series of very similar looking fields.  My destination was just far enough away that you'd think you'd maybe missed it.



Officially, it was the Lord Street Market.  But if you lived in Brockton Bay, it was just `the market'.



The market was open all week, but most people just rented the stalls on the weekends.  It was fairly cheap, since you could get a stall for fifty to a hundred dollars on a weekday and two hundred and fifty to three hundred on weekends, depending on how busy things were.  The stalls showcased everything from knick-knacks handicrafts put together by crazy cat ladies to overstock from the most expensive shops on the Boardwalk, marked down to ten or twenty five percent of the usual price.  There were ice cream vendors and people selling puppies, there was tourism kitsch and there was a mess of merchandise relating to the local capes.  There were racks of clothing, books, computer stuff and food.  If you lived in the north end of Brockton Bay, you didn't have a garage sale.  You got a stall at the market.  If you just wanted to go shopping, it was as good as any mall.



I met up with the others at the entrance.  Brian was looking sharp in a dark green sweater and faded jeans.  Lisa was dressed up in a dusky rose dress with gray tights, her hair in a bun with loose strands framing her face.  Alec was wearing a long sleeved shirt and slim fit black denim jeans that really showed how lanky he was.



``You weren't waiting long?'' I asked.



``Forever,'' was Alec's laconic response.



``Five minutes at most,'' Brian smiled, ``Shall we?''



We ventured into the market, where the best the north end of Brockton Bay had to offer was on display.  The worst of the north end was kept at bay by the same uniformed enforcers that you saw at the Boardwalk.



While Alec stopped at an isolated stall featuring cape merchandise, I commented, ``I guess Rachel can't exactly hang out with us, huh?''



Brian shook his head, ``No.  Not in a place like this.  She's well known enough that she'd catch someone's eye, and from there, it's only a short leap to figuring out who the people she's hanging with are.''



``And if she saw \emph{that}, she'd go ballistic.''  Lisa pointed to a rotund old woman carrying a fluffy dog in her arms.   It was wearing a teal and pink sweater, and was trembling nervously.  I didn't know my dog breeds well enough to name it specifically, but it was similar to a miniature poodle.



``What?  The sweater?'' I asked.



``The sweater.  The dog being carried.  Rachel would be up in her face, telling that woman it's not the way a dog should be treated.  Screaming at her, maybe threatening violence, if one of us didn't step in to handle things.''



``It doesn't take much, does it?''



``To set her off?  No it doesn't,'' Brian agreed, ``But you gradually learn how she thinks, what pushes her buttons, and you can intervene before a situation happens.''



Lisa added, ``The big trigger for Rachel is mistreatment of dogs.  I think you could kick a toddler in the face, and she wouldn't flinch.  But if you kicked a dog in front of her, she'd probably kill you on the spot.''



``I'll, uh, keep that in mind,'' I said.  Then, double checking that nobody was in a position to overhear, I figured it was as good a time to ask as any, ``\emph{Has} she killed anyone?''



``She's wanted for serial murder,'' Brian sighed, ``It's inconvenient.''



``If the courts actually gave her a fair trial, if she had a good lawyer, I think she'd get manslaughter at worst, maybe reckless endangerment.  At least for the events that happened then.'' Lisa said, her voice pitched low enough that nobody else in the crowd would pick it up, ``It happened just after her powers manifested.  She didn't know how to use her abilities, or what to expect of them, so the dog that she had with her grew into the sort of creature you've seen the others become, and because it wasn't trained, because it had been abused, it went out of control.  Cue the bloodbath.  In the time since then?  Maybe.  I know she's seriously hurt a lot of people.  But nobody's died at her hands since we've been with her.''



``Makes sense,'' I said, distractedly.  \emph{So that's one}.  Who was the other murderer in the group?



Alec returned from the stall wearing a Kid Win shirt.



``I like it,'' Lisa grinned, ``Ironic.''



We continued our roundabout walk through the market.  We were still on the outskirts, so there weren't many people around us.  Those that were around us weren't likely to overhear, unless we used words, names or phrases that would catch their attention.



``Where do we go from here?'' I asked.



``It's just a matter of handing the cash over to the boss later tonight.'' Brian picked up a pair of sunglasses and tried them on, ``He takes it, does what he needs to with the papers, and gets back to us with our pay.  Clean, untraceable.  Once we've picked up our share, we kick back for a little while, plan our next job or wait for him to offer us another one.''



I frowned, ``We're putting a lot of trust in him.  We're giving him a pretty big amount of money, and we're expecting him to come back and pay us three times that amount?  Plus whatever he feels the papers are worth?  How do we know he'll follow through?''



``Precedent,'' Brian said as he tried on another pair of sunglasses, lowering his head to examine himself in the mirror that was hanging from the side of the stall. ``He hasn't screwed with us yet.  It doesn't make sense for him to to pull a fast one, when he's already invested more than that in us.  If we were failing most of our jobs, maybe he'd keep the money to recoup his losses, but we've done well.''



``Okay,'' I nodded, ``I can buy that.''



I felt kind of conflicted about the `take it easy and wait' plan.  On the one hand, taking a break sounded awesome.  The last week had been intense, to put it lightly.  On the other hand, it sort of sucked that we wouldn't be out there on another job, since I'd be waiting that much longer for a chance on getting more details on the boss.  I'd just have to hope I could find something out tonight.



``Come on,'' Tattletale grinned at me, grabbing my wrist, ``I'm stealing you.''



``Huh?''



``We're going shopping,'' she told me.  Turning to Brian and Alec, she said, ``We'll split up, meet up with you two for dinner?  Unless you want to come with and stand around holding our purses while we try on clothes.''



``You don't have any purses,'' Alec pointed out.



``Figure of speech.  You want to do your own thing or not?''



``Whatever,'' Alec said.



``You're a jerk, Lise,'' Brian frowned, ``Hogging the new girl to yourself.''



``You get your morning meetings with her, I want to go shopping, cope,'' Lisa stuck out her tongue at Brian.



``Alright,'' Brian shrugged, ``Fugly Bob's for dinner?''



``Sounds good,'' Lisa agreed.  She turned to me, eyebrows quirked.



``I'm down for Fugly Bob's,'' I conceded.



``Don't spend so much you draw attention,'' Brian warned.



We parted ways with the boys, Lisa wrapping her arm around my shoulders and going on about what she wanted to get.  Her enthusiasm was catching, and I found myself smiling.



Murderer.  I had to remind myself.  One of these three was a murderer.





