





``We're updating your wardrobe,'' Lisa decided, after we'd left the boys behind.



``What's wrong with my wardrobe?'' I asked, a bit defensively.



``Nothing, really.  It's just very\ldots you.  Which is the problem.''



``You're not making me feel better, here.''



``You're a cautious person, Taylor.  I like that about you.  I think it's an essential addition to the group dynamic,'' she led me to a collection of stalls where there was a lot of women's clothing, and quickly drew three dresses from a rack.



``Brian's cautious.''



``You and Brian are similar, but I wouldn't say he's cautious.  He's\ldots pragmatic.  You both are.  The difference between you two is that he's been doing what he does for three years, now.  Two years of experience, before he joined the group.  So a lot of what he does is automatic.  He doesn't give a second thought to the little things he's done dozens of times already.  He takes a lot for granted.''



``And I don't?''



``You're observant, detail oriented and focused.  More than any of the others.  You watch, you interpret, and then you act with this careful, surgical precision. That's a strength and a flaw.''



``What does this have to do with my clothes?''



``Your personality is reflected in your fashion choices.  Muted colors.  Brown, gray, black, white.  If you are wearing something with color to it, you're wearing it under a sweatshirt, sweater or jacket.  Never anything that would stand out.  Never showing much skin.  While most people our age are picking clothes with the intention of defining an identity for themselves, fitting into a clique, you're focused on staying out of sight and not attracting attention.  You're being too cautious, overthinking things you don't need to, always making the call to play it safe.''



``And you want to change that.''  I sighed.



``I'm suspicious you're capable of surprising everyone, yourself included, when you drop your guard, start being bolder and improvise.  Not just when circumstances force you to.  I'm not just talking about clothes, you know.''



``I kind of got the drift.''



``More to the point, I'm seeing you alternate between the same two pairs of jeans every day, when you got a paycheck for two grand five days ago.  If I don't make you buy clothes, I don't think you're going to.''



``My dad will wonder where I got them,'' I protested, as she folded a pair of blouses over one of my arms.



``You borrowed them from me.  Or they don't fit me anymore and I gave them to you.  Or you can keep them at our place and leave him none the wiser.''



``I don't like lying to my dad.''



She ushered me into a curtained off area that served as a change room.  Through the curtain, she told me, ``I envy you that.  But if he hasn't figured out the reason your wardrobe has shrunk so much, chances are he's not going to notice if you have some new clothes.''



I was halfway through pulling off my shirt when that sunk in, ``What are you talking about?''



``Come on, Taylor.  I'd suspect you had some problems going on even without, you know\ldots a little bird whispering in my ear.''



I hurried to pull on the first dress in the pile, then opened the curtain, ``You're going to have to be a little more specific, before I can confirm or deny anything.''



``Not that one,'' she waved at the dress, a plaid number, predominantly red and white.  Annoyed, I shut the curtain.



From the other side of the curtain, she explained, ``At first I thought your dad was abusing you.  But I dropped that line of thinking pretty quick after I heard you bring him up in conversation.  It had to be a major part of your life that's sucking, though, and if it's not home then it's got to be school.  Brian and Alec pretty much agree with my line of thinking.''



``You've talked about it with them,'' I dropped my hands from the buttons of the dress and let my head thunk against the shaky plywood wall of the change room.



``It came up when we were talking about you joining the group, and we never hundred percent dropped the subject.  Sorry.  You're new, you're interesting, we talk about you.  That's all it is.''



I finished doing up the buttons of the dress and opened the curtain, ``Ever think I didn't want you prying?''



She undid the top button. ``What you want and what you need are two different things.  Cornflower blue is a keeper. Throw that one over the top.''  She pushed me back inside and shut the curtain.



``What I need is to keep\ldots'' I struggled to find a way of wording things that wouldn't raise red flags for any eavesdroppers, ``these two major parts of my life separate.''



``The suckish part and the non-suck part.''



``Sure, let's go with that.''  I found a top and a pair of low-rise jeans in the pile of clothes.



``I could help make the suckish parts suck less,'' she offered.



I swear my blood turned cold in my veins.  I could just see her showing up at school, taunting Emma.  I think the prospect of facing down Glory Girl again would spook me less.  I struggled to do up the top button of the jeans, which wasn't made any easier by my agitation.  It took thirty seconds to get the button done up, and I swore under my breath the entire time.  Where in the world had Lisa found jeans that were this tight on \emph{me?  }When I had them on, I opened the curtain and confronted her face to face.



``Having me try on clothes is fine,'' I told her, doing my level best to keep my voice calm, ``But you interfere directly in my problems, and I'm gone.''



``Just like that?''



``Just like that,'' I said, ``I'm sorry.''



She looked a little hurt, ``Fine.''  Pouting a little, she waved a hand in the general direction of my clothes, ``What do you think?''



I tried to adjust the collar.  I liked the abstract design on the right side of the shirt, but the v-neck collar came to a point near where my ribcage ended and my stomach began. ``Top is cut too low, jeans are too tight.''



``You need to get used to showing some cleavage.  Like I said, be bold in your fashion choices.''



``I'd be fine with showing some cleavage if I had anything to show,'' I pointed out.



``You're a late bloomer?'' she tried.



``My mom was a B-cup, and not always then, depending on the brand of bra.  And that was \emph{after} she went up a partial size being pregnant with me.''



``That's fucking tragic.''



I shrugged.  I'd been resigned to being broomstick thin and flat as a board pretty much from the point I'd started puberty.  I just had to look at the genetics on either side of my family to know what I was in for.



``And my condolences about your mom.  I didn't know.''



``Appreciated.''  I sighed. ``I'm vetoing the shirt.''



``Fine, you're allowed, but we're keeping the jeans.  They show off your figure.''



``The figure of a thirteen year old boy,'' I groused.



``You're taller than a thirteen year old boy, don't be silly.  Besides, whatever you look like, whatever your body type, there's bound to be someone out there who thinks you're the hottest fucking person they've ever seen.''



``Fantastic,'' I mumbled, ``There's a sketchy pedophile out there with my name on him.''



Lisa laughed, ``Go, try something else on.  But throw the jeans over the top.  I'm buying them for you, and if you never wear them, I'll have to be content with you feeling guilty about it.''



``Find me the same jeans one size larger, and I'll wear them,'' I negotiated.  Then, before she could protest, I added, ``They're going to shrink in the wash.''



``Point.  I'll go look.''



Things continued in that vein for a little while, with Lisa doing a little shopping for herself, too.  We stuck to talking about the clothes, and it was clear that Lisa was carefully avoiding the earlier topic.  When we finished, the woman at the cash totaled it up on a notepad and passed the slip of paper to us.  Four hundred and sixty dollars.



``My treat,'' Lisa said.



``Are you sure?'' I asked.



``A bribe in exchange for your silence,'' Lisa winked at me.



``About?''



She glanced at the cashier, ``After.''



It was only after we'd left the stall well behind, the pair of us laden down with bags, that Lisa elaborated. ``Do me a favor and don't go telling the gang how badly I let things slip, as far as Panacea being one of the hostages.  If they ask outright, you can say, I won't ask you to lie.  But if they don't ask, maybe don't bring it up?''



``This is the silence you're buying?''



``Please.''



``Alright,'' I answered.  I would have without the gift of clothes, but I think she knew that.



She grinned, ``Thanks.  Between them, I don't think those guys would ever let me live it down.''



``Would you let them, if the tables were turned?''



``Hell naw,'' she laughed.



``That's what I thought.''



``But about our earlier conversation\ldots last I'll say on the subject tonight, promise.  If you ever decide you \emph{do} want me to directly interfere in any of your personal stuff, just say the word.''



I frowned, ready to be annoyed, but I relented.  It was a fair offer, not pushing anything.  ``Okay.  Thank you, but I'm fine.''



``Then that's settled.  Let's go eat.''



Fugly Bobs was fast food of the most shameless kind, sold out of a part-restaurant, part-bar, part-shack at the edge of the Market, overlooking the beach.  Anyone who lived in the area had probably eaten there once, at some point.  Anyone with any sense then waited a year to give their hearts a chance to recuperate.  It was the sort of place with burgers so greasy that if you ordered takeout, you could see through the paper bag by the time you got home.  The specialty burger was the Fugly Bob Challenger: if you could finish it, you didn't have to pay for it.  It probably went without saying that most people paid.



Brian and Alec were already there when we arrived, and we ordered our food right off.  Lisa and I agreed to split a bacon cheeseburger, Brian ordered a portobello-beef double-decker and Alec matched him with a Hideous Bob – Fugly Bob's interpretation of a Big Mac.



None of us were hungry, brave or dumb enough to order the Challenger.



Brian and Alec had been sitting outside so they could spot us when we arrived.  After a brief debate, we agreed to stick to the table they'd been sitting at.  It was by the window, so we could see the TV.  It was still cool enough that most people had ventured indoors.  The only others outside were some college-aged guys, and they were sitting on the opposite end of the patio, occupied with beer and the game on the TV.  The primary benefit was that we enough had privacy to talk.



``I don't want to be a nag,'' Brian said, eyeing the piles of bags, ``But I did say you shouldn't spend so much so soon after a caper.  It's the kind of thing cops and capes watch for.''



``It's cool,'' Lisa brushed him off, ``It only raises flags with the credit card companies or banks if it's a dramatic change in a given person's spending habits.  I buy close to this amount of stuff every week or two.''



Brian frowned.  He looked like he wanted to say something in response, but he kept his mouth shut.



``So, what comes next?'' I asked.



``Dinner, then dessert,'' Alec replied, his attention on the TV inside.



``I meant in terms of our,'' I lowered my voice, ``Illicit activity.''  A quick double-check showed the college guys at the far end of the patio were still engrossed in the game.  I couldn't make out anything they were saying, and they were being loud, so I was pretty sure they couldn't hear us.



``Is there anything you \emph{want} to do?'' Brian asked me.



``Something less intense,'' I decided, ``I'm kind of feeling like I jumped into the deep end of the pool without entirely knowing how to swim.  I'd prefer to get to know my powers better in the field, figure out how to deal with situations, before I'm up against people like Lung and Glory Girl, who are literally capable of tearing me limb from limb.''



``Hah.  Something easier then.''



``If Rachel was here, she'd be calling you a wuss again,'' Alec commented.



``I'll just have to be glad she's not here, then,'' I smiled.



Our food arrived, and we used extra plates to divvy up our individual side orders so we all had a little bit of each.  That left each of us a mix of fries, sweet potato fries, onion rings and deep fried zucchini on an individual plate.  The sides alone would have been more than enough raw foodstuff for a meal on its own, but there were also the burgers themselves, each large enough to take up nearly an entire plate.  Lisa and I cut the bacon cheeseburger in half, and we each took a portion.



``I guess you're not the type that gains weight,'' Lisa eyed me.



``I have to work to put it on.''



``Dammit,'' she grumbled.



``If it's any consolation,'' I said, after taking a bite and wiping my mouth with a napkin, ``This is going to be hell on my skin.''



``That does help,'' she grinned.



Alec rolled his eyes, ``Enough with the girl talk.''



``What do you want to talk about, then?'' Lisa asked him.



He shrugged and took a bite of his burger.



I had a suggestion.  ``I know it's kind of cliche, but when people with powers get together, isn't it kind of standard to share origin stories?''



Apparently, I couldn't have picked a better way to kill the conversation.  Lisa turned away, for once without a smile on her face.  Brian and Alec gave me strange looks, not saying anything.



``What?'' I asked.  I double checked there was nobody in earshot.  ``What did I say?''

















