





Alec, surprisingly, was the one to break the nerve-wracking silence. ``Let me put it this way.  When you got your powers, were you having a good day?''



I didn't have to think long. ``No.''



``Would I be really off the mark if I guessed you were having the worst day of your life, when you got your powers?''



``Second worst,'' I replied quietly, ``It's like that for everyone?''



``Just about.  The only ones who get off easy are the second generation capes.  The kids of people who have powers.''



Lisa leaned forward, putting her elbows on the table, ``So if you needed another reason to think Glory Girl is a privileged bitch, look no further.''



``Why?'' I asked, ``Why do we go through that?''



``It's called the trigger event,'' Lisa answered me, ``Researchers theorize that for every person with powers out there, there's one to five people with the \emph{potential} for powers, who haven't met the conditions necessary for a trigger event.  You need to be pushed to the edge.  Fight or flight responses pushed to their limits, further than the limits, even.  Then your powers start to emerge.''



``Basically,'' Alec said, ``For your powers to manifest, you're going to have to have something really shitty happen to you.''



``Which may help to explain why the villains outnumber the heroes two to one,'' Lisa pointed out, ``Or why third world countries have the highest densities of people with powers.  Not capes, but a lot of people with powers.''



``But people who have parents with powers?''



``They don't need nearly as intense an event to make their powers show up.  Glory Girl got her powers by getting fouled while playing basketball in gym class.  She mentioned it in a few interviews she gave.''



``So you basically asked us to share the details on the worst moments of our lives,'' Alec said, before taking another bite of his burger.



``Sorry,'' I replied.



``It's okay,'' Brian reassured me, ``It's one of those things you only really hear about from other capes, and you only know us.  Maybe you'd hear more about trigger events if you took a university class in parahuman studies, but I doubt you'd get the full picture there.  Kind of have to go through it yourself.''



Lisa reached over and mussed up my hair, ``Don't worry about it.''



Why had I brought up origins?  It would have eventually have been my turn, and I would've had to share my own story.



Maybe I'd wanted to.



``Lisa said you guys were talking about me, talking about how you thought I was having a hard time, speculating on what it was,'' I managed to say, ``I dunno, I think a part of me wants to talk about it so you aren't coming to the wrong conclusions.  Talk about when I got my powers.  But I don't know that I can get into it without ruining the mood.''



``You already ruined the mood, dork.''  This from Alec.



Brian punched him in the arm, making him yelp.  Glaring at Brian, Alec grudgingly added, ``Which means there's no reason not to, I guess.''



``Go for it,'' Lisa prodded me.



``It's not an amazing story,'' I said, ``But I need to say something before I start.  I already said it to Lisa.  The people I'm talking about\ldots I don't want you to take revenge on them on my behalf or anything.  I need to be sure you won't.''



``You want to get revenge yourself?'' Alec asked.



I found myself at a bit of a loss for words.  I couldn't really explain why I didn't want them interfering, ``I don't really know.  I think\ldots I guess I feel that if you guys jumped in and beat them up or humiliated them or made them tearfully apologize, I wouldn't feel like I'd dealt with things myself.  There wouldn't be any closure.''



``So whatever we hear, we don't act on it,'' Brian clarified.



``Please.''



``It's your prerogative,'' he said, taking a deep-fried zucchini off of Lisa's plate and biting it in half.  She pushed her plate closer to him.



``Whatever,'' Alec said.



I took a few seconds to get a few bites of my bacon cheeseburger and composed my thoughts before I began.



``There's three girls at school that had\ldots have been making my life pretty goddamn miserable.  Doing pretty much everything they could think of to make school suck, humiliate me, hurt me.  Each of the three had their individual approach, and for a good while, it was like they were trying to outdo each other in how creative or mean they could get.''



My heart was pounding as I looked up from my plate to check the expressions on the others' faces.  \emph{This is who I am}, I thought.  \emph{This is where I'm coming from}.  When they heard about the real me, without whatever notions or ideas they'd gotten into their heads about me or how capable I was, how would they react?



``It went on for almost a year and a half before things quieted down.  Last year, around November, they\ldots I dunno.  It was like they got bored.  The pranks got tamer, then stopped altogether.  The taunts stopped, and so did most of the hate mail.  They ignored me, left me alone.



``I kept waiting for the other shoe to drop.  But I made a friend, one of the girls who had sometimes joined in on the taunting came to me and apologized.  Not one of the major bullies, more like a friend of a friend of the bullies, I guess.  She asked me if I wanted to hang out.  I was too gun-shy, told her no, but it got so we were talking before and after classes and eating lunch together.  Her approaching me and befriending me was one of the big reasons I could think the harassment was ending.  I never really let my guard down around her, but she was pretty cool about it.



``And for most of November and the two weeks of classes before Christmas break, nothing.  They were leaving me alone.  I was able to relax.''



I sighed, ``That ended the day I came back from the winter break.  I knew, instinctually, that they were playing me, that they were waiting before they pulled their next stunt, so it had more impact.  I didn't think they'd be so patient about it.  I went to my locker, and well, they'd obviously raided the bins from the girls bathrooms or something, because they'd piled used pads and tampons into my locker.  Almost filled it.''



``Ew,'' Alec interjected, putting down his food, ``I was eating here.''



``Sorry,'' I looked down at my plate, poked at a piece of bacon, ``I can stop, it's cool.''



``Finish now,'' Brian ordered me, if you can say he was ordering me gently.  He glared at Alec.



I swallowed, feeling a flush creeping across my face, ``It was pretty obvious that they had done it before the school closed for Christmas, by the smell alone.  I bent over to throw up, right there in a crowded hallway, everyone watching.  Before I could recover or stop losing my breakfast, someone grabbed me by the hair, hard enough it hurt, and shoved me into the locker.''  It had been Sophia, I was almost positive: She was the most physically aggressive of the three.  But these guys didn't need to know her name.



Why had I brought this up?  I was regretting it already.  I looked at the others, but I couldn't read their expressions.



I couldn't leave the story unfinished, after getting this far, as much as I really wanted to. ``They shut the locker and put the lock on it.  I was trapped in there, with this rancid smell and puke, barely able to move, it was so full.  All I could think was that someone had been willing to get their hands \emph{that dirty} to fuck with me, but of all the students that had seen me get shoved in the locker, nobody was getting a janitor or teacher to let me out.



``I panicked, freaked out.  My mind went someplace else, and it found the bugs there.  Not that I knew what they were, at that point.  I didn't have a sense of proportion, and with all the info my power was giving me then, my brain didn't know how to process it all.  As far as I knew, all around me, in the walls of the school, in the corners, and crawling around the filthy interior of the locker, there were thousands of these twitchy, alien, distorted things that were each shoving every tiny detail about their bodies and their fucked up biology into my head.



I sighed, ``It's hard to explain what it's like, having a new sense open up, but you can't understand it all.  Every sound that they heard was bounced back to me at a hundred times the volume, with the pitch and everything else all screwed up as if they wanted to make it as unpleasant and painful to listen to as possible.  Even what they were seeing, it's like having my eyes open after being in the dark for a long time, but the eyes weren't attached to my body, and what they were seeing was like looking into a really dingy, grimy kaleidoscope.  Thousands of them.  And I didn't know how to turn any of it off.''



``Damn,'' Lisa said.



``When someone finally let me out, I came out fighting.  Biting, scratching, kicking.  Screaming incoherently.  Probably putting on a good show for all the kids that had come out of their classrooms to watch.  The teachers tried to deal with the situation, paramedics eventually came and I don't remember much after that.



``I figured out what my power was at the hospital, while they observed me, which helped ground me, make me feel sane again.  Bugs are a lot easier to wrap your head around, when you realize they're bugs.  After a week, maybe, I was able to shut some of it out.  My dad got some money from the school.  Enough to pay the bills for the hospital stay and a little extra.  He was talking about suing the bullies, but no witnesses were really talking and the lawyer said it wasn't going to be successful without hard evidence to identify the responsible.  We didn't have the money for it, if it wasn't going to be a sure thing.  I never wound up telling my dad about the main group of bullies.  Maybe I should have, I dunno.''



``I'm sorry,'' Lisa put her hand on my shoulder.  I felt grateful that she wasn't pulling away or laughing.  It was the first time I'd ever really talked about it, and I wasn't sure I could've dealt if she had.



``Wait, this thing with those girls is still going on?'' Alec asked me.



I shrugged, ``Basically.  I went back after being in the hospital, and things were as bad as they ever were.  My so called friend wasn't making eye contact or speaking to me, and they didn't even go easy on me after seeing my, uh, episode.''



``Why don't you use your power?''  Alec asked, ``It doesn't even have to be that big.  A bug in their lunch, maybe a bee sting on the tip of their nose or on their lips.''



``I'm not going to use my power on them.''



``But they're making you miserable!'' Alec protested.



I frowned, ``All the more reason not to.  It wouldn't be hard to guess who was doing it if someone started using powers to mess with them.''



``Seriously?'' Alec leaned back in his seat, folding his arms, ``Look, you and I haven't talked all that much, maybe we don't know each other all that well, but, um, you're not stupid.  Are you honestly telling me you're incapable of finding a \emph{subtle} way to get back at them?''



I looked to Lisa and Brian, feeling a little backed into a corner, ``A little help?''



Lisa smiled, but said nothing.  Brian shrugged and considered for a few moments before telling me, ``I'm kind of inclined to agree with Alec.''



``Okay, fine,'' I admitted, ``It's crossed my mind.  I've considered doing something that couldn't be traced to me, like giving them lice.  But you guys remember how I went off on Bitch after she set her dogs on me.''



``A bit of repressed anger,'' Lisa said, still smiling.



``It's the same with these guys.  You know what happens if I do something like give them crabs?  They wind up miserable, annoyed, and they take it out on me.''



``Oh man,'' Alec laughed, ``Crabs.  You need to do that every time we go up against another cape.  Can you imagine?''



``I'd rather not,'' I made a face.  Alec's dogged tenaciousness thus far in the conversation was giving me the impression he would be hard to convince without a good reason, so I fudged the truth a little as I told him, ``While I'm controlling them, I see everything my bugs see, feel everything they feel, pretty much.  I don't want to make a regular thing of having my bugs crawl all over sweaty crotches.''



``Awww.''



``The point I'm trying to make, if you'll stop changing the subject, is that these girls would probably take their misery out on me, even if they didn't know I was doing it.  I don't trust myself to keep from retaliating, upping the ante.  You saw what happened with me and Rachel, the first time we met.  Things would escalate, I'd take things too far eventually.  Secret identity blown, or getting someone seriously hurt, like Lung was, only without the regeneration.''



``I don't get how you can sit there and take it,'' Alec said, ``Get revenge, or get one of us to get revenge for you.  Go to someone for help.''



``None of those things is an option,'' I said, with enough emphasis that I hoped my statement carried some finality, ``There's too much chance for things to go out of control if I take things into my own hands or have you guys do it for me.  As far as going to someone for help, I don't trust the system.  Not after the court case, not after talking to some of my teachers.  If it was that easy, I would have dealt with it already.''



Lisa leaned forward, ``Tell me it wouldn't be awesome if we kidnapped their leader, pulled a hood over her head, dragged her into a van and dropped her off in the woods at midnight, ten miles out of town, with nothing but her skivvies.''



I smiled at the mental image, but I shook my head as I said, ``That's exactly what I'm talking about.  It's going too far.''



``They shoved you into the grossest locker ever and locked the door!'' Alec looked at me like I was trying to argue the earth was square.



``Leaving her in the middle of nowhere without any clothes on is practically inviting her to be molested by the first trucker to see her,'' I pointed out.



``Fine,'' Alec rolled his eyes, ``So we tone it down some.  Drop her off with no shoes, no cell phone, no wallet, no spare change, nothing she could use to negotiate her way home.  Make her hike it.''



``That would still be risking getting her assaulted,'' I sighed, ``Pretty girl walking down the side of the road at night?''



``They've assaulted you!''



``It's a little different.''



``The only difference I see is that they deserve it and you didn't.  I mean, I'm not smart like you guys are, so maybe I'm missing something.''



I shook my head, ``You're not missing anything, Alec.  We're looking at this from two very different perspectives.  I don't really believe in that whole `eye for an eye' business.''



I was beginning to feel like I was getting control of the conversation again.  Then Alec dropped his bombshell.



``Then why the fuck are you a supervillain?''



``Escape.''  The word left my mouth almost immediately, before I'd had a chance to even think about what it meant.  I couldn't have taken the time to think before speaking, or they might have known something was up.  Lisa almost certainly would have.



A few tense moments passed, and I chanced a look at Lisa and Brian.  Lisa was watching the dialogue, a small smile on her face, her chin resting on her palm.  Brian was kind of inscrutable, arms folded in front of him, no real expression on his face.



I explained, ``I can deal with real life, if I can leave it behind for this.  Kicking ass, making a name for myself, hanging out with friends.  Having fun.''



It kind of surprised me, but I realized what I was saying was true, so I didn't even need to worry about tipping Lisa off.  A second later, I realized I might have been a little presumptuous.  ``I mean, assuming that we \emph{are} frien--''



``If you finish that sentence,'' Lisa warned me, ``I'm going to slap you across the head.''



I felt the heat of a flush in my cheeks and ears.



``Yes, Taylor, we're friends,'' Brian said, ``And we appreciate, or at least, \emph{I} appreciate that you trusted us enough to share your story.''



I wasn't sure what to say in response to that.  The fact that he'd heard it and didn't give me a hard time, it meant a hell of a lot to me.  Only Alec was really getting on my case about it, and he wasn't doing it in a mean spirited way.



Brian frowned.  ``Don't suppose either of you are going to share your stories?''



Alec shook his head and stretched his arms above his head before resting them on his full stomach, his silence answer enough.



Lisa, for her part, grinned and said, ``Sorry.  I like you guys, but I'm going to need a few drinks before I share that particular tidbit, and I'm not legal to drink for a few years yet.''



``Doesn't seem fair that Taylor's the only one sharing,'' Brian pointed out.



``I- I didn't tell my story because I expected you guys to reciprocate,'' I hurried to add, ``Really, it's fine.''



``You're volunteering, then?'' Lisa asked Brian, ignoring my protests.



Brian nodded, ``Yeah, I guess I am.''

















