





An evening crowd had started to file into Fugly Bob's, large groups that were grabbing beers and moving tables together to accommodate their individual crowds.



As one group began dragging tables into one long row in the middle of the patio, not far from where we were sitting, Brian asked, ``Want to go?  I'll share my bit on the way back.''



There were no arguments, so we paid our bill and left.  Brian was gracious enough to carry some of Lisa's and my bags, in addition to his own, lightening our load.  The Market itself had mostly emptied, with the various merchants and shoppers having left to get their dinners.  Only the stalls and venders that were selling food were sticking it out.  Brian apparently deemed it safe to begin.



``For background, I guess it's important to mention that my parents split up when I was thirteen,'' Brian told us, ``I went with my father and my sister Aisha went with my mom.  Aisha and I kind of stayed in touch, but there's four years difference in our ages, our interests were completely different, so there wasn't a lot to say.  I'd send her a text message about how my day at school had been painfully dull, and a few days later, she'd send me an email about a cartoon she liked.  Or she'd ask me for advice on what to do when she got an F on a spelling test.



``We weren't close.  It wasn't really possible, since I was living at the south end of the city and she was up here.  But one night, I got a text from her.  Two words: `Help me'.  I called, but the line was busy.  To this day, I don't know why I took it so seriously, but I got over to my mom's place as fast as was humanly possible.  Ran out the front door, sprinted two blocks to Lord Street, downtown, and grabbed a cab.  Left the cab driver shouting for his money as I charged through the front door of my mom's place and found my sister.



``She'd been crying, but she wasn't saying what was wrong.  I didn't bother asking a second time.  I gave her a hug, picked her up and started to leave.  A man I didn't recognize got in my way.  My mom's new boyfriend.



``I \emph{knew} he was the reason she had texted me for help, from the moment I saw her reaction.  Maybe I'd suspected there was something going on even before that, from the way her emails and texts had changed in tone.  It would explain that gut feeling I'd had that made me get over there as fast as I did.  I saw her shrink back, I felt her hold me tighter, and I went cold inside.



He paused a second, just walking in silence.  I almost thought that he was done, somehow, until he suddenly turned to me.  ``I think I mentioned, Taylor, that my father had been a boxer, while he was in the service?''



``Yeah,'' I replied.



``Well my father is a hard man.  Not the kind of man that's meant to raise a son alone.  I wouldn't say he was abusive, but there's never been any warmth to him, no charming anecdotes, no fatherly wisdom, no throwing baseballs in the backyard.  The extent of our bonding was in the gym, him holding the punching bag in position while shouting at me that I was doing something wrong, staying grimly quiet if my form, my timing, the raw power of my hits were all flawless.  Or we'd be in the ring, with boxing helmets and gloves on, a thirty five year old man in peak physical condition barely holding back against his fifteen year old son.  He just expected me to keep up or take the hits, and I didn't have much choice in the matter.



``So even if I was only fifteen, I was tall for my age, I was fit, and I knew how to throw a punch.  I didn't say a word, didn't make a sound.  I put my sister down and beat my mother's boyfriend within an inch of his life, my mother screaming and wailing the entire time.  When I was done, I picked my sister up and returned to the cab.  We went to my father's that night, and we went to the police station in the morning.''



``When you throw a punch barehanded, it doesn't leave your hands pristine.  A few good swings, you connect solidly with someone's face, someone's teeth, and it tears the fuck out of your knuckles.  It was at my father's place that night, washing and cleaning my hands, when I saw it.  It wasn't just blood leaking out of my torn up knuckles, but there was the darkness too, like wisps of really black smoke.  You hear about the trigger event, you might think it's all about rage or fear.  But I'm a testament that it can be just the opposite.  I didn't feel a fucking thing.''



``Wow,'' I said.



``That's my story,'' he said.



``Um, I can't think of a nice way to put this, but why aren't you in jail, after thrashing that guy?''



Brian sighed, ``It was a close call, but the guy I beat up had violated the terms of his probation by not going to his narcotics anonymous meetings and Aisha backed me up as far as us saying, well, it was well deserved.  He came across as the bad guy more than I did.  He got six months in jail, I got three months of community service.''



``And you've been as good as gold ever since, haven't you?'' Lisa grinned.



Brian smiled at that.  ``These guys know already, but I don't think I mentioned it to you,'' he said to me, ``I got into this for Aisha.  My mother lost custody of her after child services stepped in, so Aisha's living with my father now.  Problem is, he's not an ideal parent.  It's been nearly three years, and he still doesn't know what to do with a daughter, so they mostly ignore each other.  But she's acting out, getting into trouble, and she needs someone watching over her that isn't him and isn't our mother.  I turn eighteen in June, and when I do, I plan to get my mother and father's parental rights terminated and apply to become Aisha's guardian.  To do that, I'm going to need money.''



``Thus his current, rather lucrative, form of employment,'' Lisa pointed out.



Brian stuck his hands into his pockets, ``My father has given me his blessing as far as my taking custody of my hellion of a sister.  My mother made it clear she's going to fight it every step of the way.  That means legal fees.  It means paying a private investigator to get proof that my mother hasn't kicked her habits as far as the drugs and the fucked up boyfriends.  I'll need an apartment that's going to pass inspection, with a space ready and set aside for Aisha.  More than anything, I've got to present myself as someone that's financially secure and responsible enough to make up for the fact that the other option is Aisha's own mother.''



``The boss is helping on that last bit,'' Lisa said, ``The allowance and a share of the other income Brian is getting is coming back to him in the form of a paycheck from a legitimate company, and the manager of said company is both willing and able to provide a glowing recommendation on his behalf.''



``Which I'm less than thrilled about,'' Brian admitted, ``It's\ldots convenient, I don't know how else I'd manage it, but I don't like being so reliant on someone I don't know at all.  He could walk away with that forty thousand dollars, I'd deal.  But if he fucked me on this\ldots''



``You said it earlier,'' Lisa assured him, ``He has no reason to.''



``True.  It doesn't make me feel much better.''



``I think what you're doing is very noble,'' I said.



``No,'' Brian almost sounded offended at the idea. ``I'm just doing what I have to.  She's family, you know?''



``Yeah,'' I said, ``I know.''  I could understand how family was a priority.



We fell silent for a minute or two, only partially because some mothers with oversize strollers had turned a corner and were walking in front of us, putting them easily in earshot.  The other reason was that there hadn't been too much more to add to the conversation.



I was relieved when the two moms parked their strollers and stopped to look in a store window, because it let us get ahead of them.  Groups of people who take up the entire sidewalk so you have to step onto the road to go around them are a definite pet peeve of mine.  Oblivious people who block the entire sidewalk and walk slowly enough that you're forced to dawdle, yet fast enough that you \emph{can't} walk around them?  They make me fantasize about bringing swarms of bees down on their heads. Not that I would actually do it, of course.



When we were free to talk again, I found myself struggling to think up a new topic of conversation.  I glanced at Brian, trying to gauge how he was feeling after telling his story.  Was he really okay, or was he just really good at repressing his feelings?  He looked totally normal, as relaxed as one could expect from someone who was carrying as many shopping bags as he was.



``Hey, what did you buy?'' I asked him.



``Some stuff for my apartment.  Placemats, a piece of art I gotta to put in a frame.  Kind of boring.  I found a neat statue, the guy said it was a concept sculpt he did for a horror movie that never panned out.  I was thinking it had a freakish looking face, and since I'm thinking of updating my costume, I was considering using the statue as an inspiration for a new mask.  Move on from the skull.''



``You'll have to show me,'' I said.



``Actually,'' he paused, ``You're the person I was most interested in showing it to.  Your costume is pretty cool, and I was wondering if you had any suggestions on where to go?''



``Where?''



``For costumes.''



I stared at him blankly for a few seconds, trying to piece together what he was saying.



``Having my power is really frustrating, sometimes,'' Lisa complained, ``It's like being the only person with eyes in the land of the blind.  Taylor, Brian is asking you where you bought your costume.  Brian, she didn't buy her costume.  She made it from scratch.''



``No shit?'' His eyebrows raised.



``It's spider silk,'' I said, ``So it's got a tensile strength that's only a hair less than steel, but it's a fraction of the weight.  It's not as strong as kevlar, but it stretches, which means it's going to handle regular wear and tear better than a costume made with steel, kevlar or rubber would.  Making it was kind of complicated, because of how I needed to manage the spiders and weave it, but I basically had the spiders do the work while I concentrated.''



Brian nodded, ``That's pretty damn cool.  Would you make me one?''



That gave me pause.



``I wouldn't expect you to do it for free,'' he added.



``How much are we talking?'' I asked.



``Name a price.''



I thought on it.  ``Two thousand?''



He chuckled, ``No discount for me being a team member and a friend?''



``That is with a discount,'' I said, ``It takes time, long hours of having to be in general proximity to the bugs as they work, which I can't do all the time, because my dad would see if I left them out while he was home.  Plus I have to rotate the spiders so I constantly have a fresh supply of silk, but I can't have so many in the neighborhood that people would notice\ldots it's not easy.''



``If that's the big issue, then change locations,'' Lisa suggested.



``To where?  It has to be a place I'm spending a lot of time, some place with room to work, where I can keep a few tens of thousands of spiders without anyone noticing.''



``The loft?'' Lisa shrugged, ``Or to be more specific, the area under the loft?''



That stopped me.  It made so much sense I could have kicked myself for not thinking of it the instant Lisa suggested changing locations.



``Woah, woah, woah,'' Alec cut in, ``Tens of thousands of spiders?''



``If I want the work to be relatively quick,'' I said, ``Yeah, we're probably talking about that much.  Especially since I suspect Brian is going to want something a little heavier. The floor under the loft could definitely work.  I mean, it's not like a few more cobwebs will attract attention if anyone sticks their head in, right?''



Alec ran his fingers through his hair, which I took to be a sign of stress or worry.  It was a rare thing, to see him as anything but bored or half distracted.  As if to confirm my thoughts, he said, ``I don't want tens of thousands of spiders just lurking below me, making spider noises and climbing upstairs to crawl on me while I sleep.''



I tried to reassure him, ``Black widows don't tend to roam, and they're more likely to devour each other than they are to bite you.  I mean, you wouldn't want to provoke one--''



``Black widow spiders?'' Alec groaned, ``This is the point where you say you're messing with me.  It's cool, I can take a prank.''



``They have the strongest dragline silk you'll get from any spider around here,'' I said, ``I'd love to get my hands on something better, like a Darwin's bark spider.  They've got the strongest silk of any arachnid or worm out there.  It could make fabric five times as tough as kevlar.  I'd ask our boss to see about getting me some, if I thought they could survive in this mild climate.''



``You're not kidding about the black widow spiders.''



``Remember the ones I brought to the bank robbery?  I brought them from home.''



``Fuck,'' Alec said, then he repeated himself, ``Fuck. And now Brian's going to insist on that costume, so this is probably going to happen.''



``Arachnophobic?'' I asked, just a little surprised his reaction was so strong.



``No, but I think anyone would be spooked by the idea of tens of thousands of black widow spiders being in the same building as them.''



I considered for a moment, ``I could have cages, if it would give you some peace of mind.  It probably makes sense to have it anyways, since they're territorial, and would kill each other when I wasn't there.''



``We'll work something out,'' Lisa grinned, ``Think you could micromanage enough to make me one too?''



It struck me that I was thinking seriously about putting together some high quality costumes for villains.  I wasn't sure how I felt on the subject.



``I can micromanage my bugs enough to make two at once, sure\ldots but it's really just such a pain in the ass.  I was so relieved to be done my own costume, I'm not looking forward to the idea of doing two more.''  All true enough.  ``Let me think on it?''



``One thousand five hundred,'' Brian said, ``I'll go that high, now that we've come up with a way to maybe handle the logistics of it.  I think it's a fair offer.''



``Okay,'' I said.  Money didn't hold any sway over me, really.  I mean, big numbers could make my eyes widen, but at the end of the day, I had no plans to spend my ill-gotten gains.



All in all, it took us maybe an hour to get back to the Loft.  I didn't mind.  My training meant the hike didn't tire me out much, and the company was good.



As we made our way into the building and the others headed up the stairs, I stayed behind to look at the factory area on the first floor.  If I could maybe secure some plywood to the frames where there had been treadmills, it would mean I would have several long countertops for my bugs to work on.  Add some sort of cage at the back, to house them\ldots but where would I find the sort of grid of cages or containers that could house thousands of individual spiders?



It was something I could figure out.  Whether I settled on egg cartons or built the entire thing with the help of bug labor, I knew it was doable somehow.



The question was, did I \emph{want} to do it?



I made my way upstairs, deep in thought.



``Where's Rachel?'' Brian asked, as he returned from the other end of the loft, Brutus and Angelica trotting behind him, tails wagging. ``Only two of her dogs are here.''



``We're twenty minutes later than we said we'd be,'' Lisa pointed out, ``Maybe she went ahead?''



``You guys get ready,'' Brian directed us, ``We told our employer we'd hand the cash over at some point tonight, and if we take too long, it's going to reflect badly on us.  I'll take care of calling Rachel to see what's up, since it doesn't take me as long to get my stuff on.''



Alec, Lisa and I headed towards our individual rooms.  After shutting the door, I got my costume from the bottom drawer of my bedside table.  I laid it out on my inflatable mattress, then gathered and lined up my arsenal for my utility compartment: pepper spray, knife, telescoping combat baton, notepad, Epipens, a change-purse with some spare change and a twenty inside and an unused, disposable cell phone.  Everything I'd been able to think of, for what I'd want to keep with me.



Pen, I realized.  It was a little thing, but a notepad did me little good without a pen.  I headed for the dresser and stopped short.



On top of the dresser, there was a crystal.  Except crystal was the wrong word.  It was a teardrop shaped piece of amber, polished smooth, almost a foot tall, set into a stone base so it stood upright.  Inside was a dragonfly.  The dragonfly was so large it almost didn't fit – it wouldn't have fit, even, if the wings hadn't curled inward at the tips as the amber set.  Where the light from the loft's windows touched the crystal, it cast the top of the dresser and some of the wall in deep shades of yellow and orange, with hints of dark blue where it passed through the dragonfly's translucent wings.



There was a note beside it.  `Saw it, seemed very you.  Consider it a belated welcome present.  Brian.'



I was stunned.  He must have left it while I was still downstairs.  I hurried to get into my costume, found a pen in the dresser and put the contents of my utility compartment in place.  When that was done, I pulled on some jeans, a sweater and a jacket over top of the costume, finishing up with a nearly empty backpack to cover the slight hump of the armor on my back.



It was only after I was totally ready that I headed out of my room and found Brian on the couch.  While I was sure he'd be gracious either way, I was assuming he would appreciate it more if I got ready first and then thanked him, instead of the other way around.



He was still in the living room, pulling on his leather motorcycle jacket over a protective vest.



``I-uh, don't know what to say.''



His forehead creased, ``Is it okay?  I was thinking, maybe giving you a rock with a dead bug inside it wasn't the nicest--''



``It's perfect,'' I interrupted him, ``Really.  Thank you.''  I never knew what to say when getting a gift.  I always worried my thanks sounded false, forced or sarcastic, even when they were genuine.



Impulsively, I gave him the briefest of hugs.  It seemed like the only way I could make my gratitude clear.



``Hey!'' a voice from behind me startled the wits out of me, ``No romance in the workplace!''



I turned around to see Alec and Lisa standing in the hallway, grinning.  In Lisa's case, grinning more than usual.



I must have turned beet red.  ``It's not, no, I was just thanking him for--''



``I know, dork.  I was with him when he bought it.''



Mercifully, Lisa changed the subject, ``Any word from our resident sociopath?''



Brian frowned, ``No.  Her phone is out of service, which it shouldn't be, since I was the one who turned it on, activated it and gave it to her earlier today.  Something's up.''



The good natured mood from moments before was gone.  We exchanged looks between us, and nobody was smiling now.



``I think\ldots'' Brian said, weighing his words carefully, ``It would be a very good idea to check on the money, ASAP.''





