





Sunsets are always best after a spell of bad weather.  Today was no exception.  Following the day and a half of heavy rain we'd just suffered through, the sky was turning vivid shades of orange and crimson, with purple highlights on the thin clouds that were moving briskly in the strong wind.  It looked especially amazing as we approached the water of the Bay, but none of us were really in a mood to appreciate it.



It was like we were an entirely different group of people from the group of friends that had walked from the market to the loft.  There was no conversation, no joking, no bonding.  We were all thinking the same thing: that something was wrong, that something had happened.  Nobody voiced their suspicions, though, as if there was the unspoken agreement that we would only make it come true by saying it aloud.



In silence, we caught the bus at the ferry and got off at the Trainyard, the part of the Docks that sat opposite to the Boardwalk.



As a group, we walked a half block from the bus stop, around the back of a derelict building, and stripped out of our civilian clothes.  The storage facility was just a block from the Trainyard.  Just past the chain link fence,  I could see long abandoned boxcars sat like oversize, crumbling tombstones, overgrown with weeds, surrounded by discarded bottles and makeshift shelters.  The entire area was desolate, empty.  It was hard to say why the bus even came this way.  I supposed maybe there was a skeleton crew of employees maintaining the rail for the trains that happened to pass through.



We descended into the maze.  Each storage locker was only about ten feet by ten feet across, but there were hundreds of them, each one joined to the one beside it, organized into disorganized rows of ten or twenty brick shacks.  It was a common enough sight; places like this were scattered all over Brockton Bay.  Decades ago, as unemployment rates skyrocketed, people had started using the storage lockers as a place to live.  Some enterprising individuals had caught on and storage blocks much like this one had appeared in the place of dilapidated warehouses and parking lots.  It was, in an off the books sort of way, the lowest budget living accommodations you could find, a way for people who'd had apartments and homes of their own to keep their most cherished possessions and sleep on a bed at night.



But things turned sour.  These storage facilities became drug dens, gathering places for gangs and areas where the crazies would congregate.  Epidemics of the flu and strep throat had swept through these `neighborhoods' of closely packed, unwashed and malnourished groups of people, and left people dead in their wake.  Some who didn't die to sickness were knifed for their belongings or starved, and corpses were left to rot behind the closed doors of their rented storage lockers.  In the end, the city cracked down, and the lockers fell out of favor.  By then, the local industry had crashed enough that the homeless and destitute were able migrate to the abandoned warehouses, factories and apartment blocks to squat there instead.  The same general problems were still there, of course, but at least things weren't so densely packed into a volatile situation.



That left these sprawls of storage lockers scattered over the city, particularly in the Docks.  They were largely unused, now, just row upon row of identical sheds with faded or illegible numbers painted on the doors, each with a corrugated steel roof bolted securely on top, slanted just enough that people wouldn't be able to comfortably walk or sleep on top of them.



``We're looking for thirteen-oh-six,'' Grue spoke, breaking the silence that had hung over us for half an hour.  It took us a few minutes to find.  There wasn't really any rhyme or reason to the layout of the lockers or the numbering.  Probably, I guessed, the lockers had been set down where there was room, and given the first number that was available.  The only reason we found the locker as fast as we did was that Brian had been here before with Rachel.  The vastness of the space and the disorganization was a large part of the reason we had stashed the money here, of course.  If we had trouble even when we knew where we were going, then someone who knew the number and got the key from us would find it even more time consuming.



While Grue fiddled with the lock, I glanced down both ends of the alley we were in.  Except for a forklift parked a short distance away, it was eerily quiet.  A ghost town, I thought.  If ghosts existed, they would reside in a place like this, where so much misery, violence and death had occurred.



``Shit,'' Grue said, as the door swung open.  My heart sank.



I stood on my toes to get a look inside.  The locker housed only a broad smudge in the thick layer of dust on the floor, a single lightbulb dangling from a power cord, and a dark stain in the corner.  No money.



``I vote we kill her,'' Regent said.



My eyebrows went up, ``You think it was Bitch?  Would she just take the money and run?''



``If you asked me five hours ago, I would've said no,'' Regent replied.  ``I would have told you, sure, she's a loose cannon, she's reckless, crazy, she's easily pissed off and she'll hospitalize those people who do piss her off\ldots but I'd have said she's loyal, that even if she doesn't necessarily like us-''



``She doesn't like anyone,'' I interrupted.



``Right, she doesn't like anyone, us included, but we're the closest things she has to friends or family, besides her dogs.  I wouldn't have thought she'd throw that away.''



``She didn't,'' Tattletale spoke, ``It wasn't her.''



``Who was it?'' Grue asked.  The haunting echo of his voice had an edge of anger to it.



``A cape,'' Tattletale replied, almost absentmindedly, as if she was focusing on something else, ``Someone who can pick locks.  That door wasn't forced.''



``A villain?'' I asked.



``A villain,'' Tattletale echoed me.  I couldn't tell if she was clarifying what I'd said or if she was just echoing my words while she paid attention to something else.  ``More than one.  And they're still here.''



A soft clapping answered her.  It was slow, unenthusiastic to the point of being sarcastic.



``Brilliantly deduced,'' the same person that had been clapping spoke out.  As Tattletale whipped her head around, I took a few steps back from the storage locker, to get a better look at the two people who stood on the roof.



They were standing with one leg higher than the other, to keep from sliding off the angled roof, and both were wearing identical costumes.  The costumes sported blue man-leotards with broad belts cinched around their waists, skintight white sleeve and leggings.  Their hoods were elastic, clinging to their heads so they left only a window for the face, and each sported a single white antenna.  Of all colors, their gloves, boots and the balls at the top of their antennae were \emph{bubblegum pink}.  Their faces were obscured by oversize goggles with dark lenses.



Other than their costumes, though, they couldn't have been more different.  One of the figures was scrawny, with a weak chin and a bad slouch.  The other had a sculpted physique, broad shouldered and tall, the lines of his muscles clearly visible through his skintight costume.



``\"{U}ber and Leet,'' Tattletale greeted them, ``I can't tell you two how relieved I am.  For a few seconds, I thought we had something to be worried about.''



``Rest assured, Tattletale, you do,'' \"{U}ber proclaimed.  He was the sort of person who proclaimed, announced, broadcasted and declared.  Just like Grue's power altered his voice to make him sound haunting and inhuman, \"{U}ber's power made him sound like the guy who narrated trailers for action movies or late night commercials.  Overdramatic, intense about everything he said, no matter how mundane.  Like someone overacting the role of a gallant knight in a kid's movie.



I looked around for what I thought of as the snitch.  I finally spotted it as a small round shadow against the backdrop of the sunset-red sky, just above the glaring sliver of sun.  It was a camera, mounted in a golden sphere the size of a tennis ball.  It was capable of moving like a hummingbird, staying safe, always recording.  \"{U}ber and Leet streamed all of their costumed activity online, so people could tune in whenever to see what they were up to. I was pretty sure they had a time delay, so events that the camera recorded would play out online in a half hour to an hour.



I could admit I had watched myself, a couple of times, which was how I knew about the `snitch'.  Each time I'd tuned in, I had been surprised to see there were thousands of viewers.  I'd stopped because it wasn't feel-good watching.  They were real underdogs, struggling to succeed, which made you feel sorry for them, made you want to root for them, until they did something despicable.  Then you found yourself looking at them in a negative light, looking down on them, cheering whenever they failed.  It felt a little too much like I'd been looking at them in the same way Emma, Madison and Sophia looked at me, and that had been a major turn-off.



After spotting the camera, which was no doubt positioned to catch a view of us looking up at the two villains, our shadows long behind us, I turned my gaze back to the pair.  With my power, though, I sent a collection of flies to congregate around the camera.  It didn't take long for the camera to start going spastic in the periphery of my vision, as if it were trying to shake them off.  I smiled behind my mask.



Leet frowned and turned to the camera, ``Is that really necessary?''



``You fucked with us,'' I replied, ``I fuck with your subscriber base.''



Tattletale and Regent grinned and chuckled, respectively.  Only Grue stayed quiet.  He was standing very still, but the darkness around him was roiling like a stoked fire.



``What's the theme tonight?'' Regent called out, ``Your costumes are so terrible, I can't look directly at them long enough to try and figure it out.''



Leet and \"{U}ber glared at him.  Their entire schtick was a video game theme.  With every escapade, they picked a different video game or series, designing their costumes and crimes around it.  One day it would be Leet in a Mario costume throwing fireballs while \"{U}ber was dressed up as Bowser, the two of them breaking into a mint to collect `coins'.  Then a week later, they would have a Grand Theft Auto theme, and they would be driving through the city in a souped up car, ripping off the ABB and beating up hookers.



Like I'd said.  Despicable.



\"{U}ber approached the edge of the roof and stabbed his finger in Regent's direction, ``You-''



He didn't get to finish.  Regent swung his arm out to one side, and \"{U}ber lost his footing.  I joined the others in stepping back out of the way as he fell face first onto the pavement at the base of the locker.



``Too bad you're fucking with the camera,'' Regent commented, tilting his head in my direction, ``I would have liked to see how many hits that clip would have gotten on Youtube.''



``Give me some advance warning next time,'' I told him, ``Maybe a hand signal?''



We had backed away from the locker as \"{U}ber fell, and we retreated another few steps as he stood.  Leet hopped down to stand beside him.



``The money,'' Grue spoke, ``Where is it?  How did you find it?''



``Your fifth team member led us straight to it.  Lucky happenstance, really,'' Leet grinned, ``As for how we found \emph{her}\ldots'' he trailed off.



Grue spoke in a low voice that wouldn't carry to the pair of villains, ``They did something to Bitch, they've got the money.  If we don't get a decisive victory here, our reputation is fucked.''



``No holds barred?'' Tattletale murmured.



``Leave one of them in a state to be interrogated.  Make it Leet, since \"{U}ber's powers make him annoying to keep contained.  Give him a chance and he can figure out how to do anything like he's a goddamn expert at it, and that probably extends to escaping from ropes or handcuffs.  Alright?''



``I'm game,'' I answered.  I was surprised at how excited I was.  This was the sort of thing I had put on a costume to do.  Sure, the context wasn't what I would have chosen, but going up against bad guys?



I smiled behind my mask and reached out for my bugs.





