





We weren't the only ones who were discussing strategy.  As I turned my full attention to the pair, I saw \"{U}ber and Leet were muttering to one another.



When they realized I was looking at them, they stopped talking.  \"{U}ber wiped again at the blood under his nose and took a step forward.  ``Enough talking.''



I wished there were more bugs in the area.  The storage facility made for a disappointing selection.  Bugs had to live off something, and there was little around here except pavement, concrete and brick.  That left me only cockroaches and moths that had lived off of the contents of the lockers they could access, and spiders that dwelled in the dark corners.  However lame the pair of them were, I wasn't happy about going up against two supervillains with so little at my disposal.



I didn't get a chance to dwell on it, because \"{U}ber charged us.  I hurried to get out of his way.  \"{U}ber's power made him talented.  It didn't matter if it was playing the harmonica, parkour stunts or Muay Thai, he could pull it off like he'd been working on it for hours a day for most of his life.  If he really focused on it, the way I understood it, he could be top notch.



In short, there was no fucking way I was going to let him get close to me.



Grue had the opposite perspective.  He stepped forward and then disappeared as darkness swelled around him.  A second later, \"{U}ber stumbled out of one side of the cloud, landed on his rear end, and then did a fancy spinning kick maneuver to bring himself to his feet again.  The juxtaposition of clumsiness and technique was outright bizarre.



My bugs were gathering nearby, now, but very few of them were useful.  Somewhere in the periphery of my consciousness, I'd connected to a fledgling wasp nest hanging from a storage locker near the Trainyard.  They were more useful, but extricating them all from the nest and bringing them to my location would take a minute.  I brought the rest of the bugs into a small swarm nearby, letting the group grow until I had use of them.  Both Kid Win and Lung had obliterated my swarm when I'd attacked them, and I couldn't risk being more or less powerless if Leet pulled a similar stunt.



Leet stepped in as \"{U}ber circled around us.  Reaching behind his back, Leet retrieved what looked like an old school bomb; Round black iron casing with a lit fuse sticking out of it.  The way the light bounced off it made it look wrong, though.  Like it was a picture of a bomb instead of a real one.



Regent waved his hand, and the bomb slipped from Leet's grip, rolling a few feet.  Leet's mouth opened into a round `o', and he bolted.  \"{U}ber wasn't far behind.



As he joined the rest of us in running for cover, Regent half turned to thrust out one hand.  \"{U}ber stumbled and fell just ten feet from the armed explosive.



The blast radius was thankfully small.  The shockwave that rippled past us didn't even make me lose my footing.  \"{U}ber, though, went flying.



Leet watched his friend roll with the impact, try to stagger to his feet and fall again.  He turned to us with his face etched in hard lines of anger.



``I keep wondering when you guys are going to give up,'' Tattletale grinned, ``I mean, you fail more often than you succeed, you make more cash from your web show than you do from actual crimes, you've been arrested no less than three times.  You're probably going to wind up at the Birdcage the next time you flub it, aren't you?''



``Our mission is worth it,'' Leet raised his chin – inasmuch as he had one – a notch.



``Right,'' Tattletale said, ``Spreading the word about the noble and underrated art form that is video games.  That's from your website, word for word.  People don't watch your show because they think you're righteous.  They watch because you're so lame it's funny.''



Leet took a step forward, fists clenched, but \"{U}ber called out, ``She's provoking you.''



``Damn right I am.  And I can do it because I'm not scared of you.  I don't have any powers that are useful in a fight, and you guys don't intimidate me in the least.  A guy who's good at everything yet still manages to fuck up half the time, and a Tinker who can only make stuff that breaks comically.''



``I can make anything,'' Leet boasted.



``Once.  You can make anything once.  But the closer something you invent is to something you've made before, the more likely it is to blow up in your face or misfire.  Real impressive.''



``I could demonstrate,'' Leet threatened, jabbing a thumb over his shoulder.



``Please don't.  I hear the carbonized ash of geek is hell to get out of a costume.''



``You say geek like it's a bad thing,'' \"{U}ber said, in his characteristically overdramatic tone, ``It's a badge of honor.''



``Among geeks, sure,'' Regent replied, ``But there's clowns out there that consider being a clown to be a noble calling, while the rest of us just laugh at them.  Catch my drift?''



``Enough,'' Leet growled, ``It's obvious you're trying to antagonize us--''



``I just admitted it.  That's not obvious.  That's fact,'' Lisa pointed out.



``We won't be baited!'' Leet raised his voice, I think it's time for our grand reveal, our guest--''



He was cut off as Grue blasted him in the face with a cloud of darkness.  Leet stepped out of the cloud, sputtering.



``They're laughing at you, Leet,'' Tattletale heckled him, ``You're trying to be all dramatic, all intense for your viewers, and they're just sitting at their computers, snorting over how much you suck.  Even \"{U}ber is laughing at you behind your back.''



``Shut up!'' Leet spat the words, glancing over his shoulder at his teammate, ``I trust \"{U}ber.''



``Why are you even with this guy, \"{U}ber?'' Regent asked, ``I mean, you're kind of lame, but you could at least accomplish something if he wasn't fucking up half your jobs.''



``He's my friend,'' \"{U}ber replied, like it was the simplest thing in the world.



``So you don't deny he's holding you back.'' Lisa pointed out.



``Shut up!'' Leet roared.  Except he didn't have a very deep voice, so it was probably closer to a screech.  He pulled out another bomb and flung it at us before Regent could make him fumble again.  We scattered, with Regent, Tattletale and I running away while Grue shrouded both himself and \"{U}ber in darkness.



As I scrambled for cover, I directed my bugs to attack Leet.  He'd done something different this time, because the bomb didn't take half the time the first bomb had before it detonated.  It caught me off guard, and I didn't get a chance throw myself to the ground as a result.  The blast caught me full in the back.



The air and the fire that rolled over me wasn't hot.  That was the most surprising thing.  That wasn't to say it didn't hurt, but it felt more like getting punched by a really big hand than what I would have thought an explosion would feel like.  I could remember Lung's blasts of fire, Kid Win shattering the wall with his cannon.  This felt\ldots false.



``The bombs are fake?'' I asked aloud, as I picked myself off the ground.  I ached, but I wasn't burned.



``They're solid holograms,'' Tattletale said, ``Actually pretty neat, if you ignore how ineffective they are.  I guess he couldn't make real bombs without fucking up.''



Leet snarled, though it was hard to say whether it was Tattletale's words or the moths, wasps and cockroaches that had settled on him.  As I'd suspected, they weren't doing much.  Even crawling for his nose and mouth, they didn't really slow him down.  Maybe there was a downside to getting him furious, like Tattletale and Regent were intent on doing.



He whipped out two more bombs and Regent was quicker this time, snapping his hands out.  Leet recovered before he dropped the bombs, and pulled his arms back to throw them.  Regent was ready, though, and one of Leet's legs jerked out from under him.  He fell to the ground, the bombs rolling only a few feet from him before going off.



He slammed into a door hard enough I thought he might have managed to kill himself.  Before I could approach and check his pulse, though, he began struggling to get to his feet.



``Good thing you made those things nonlethal,'' I muttered, half to myself, ``You're one for four.''



Glaring at us, he reached behind his back again and withdrew a sword.



``Link's sword?'' Regent taunted him, ``That's not even from the right game.  You're breaking theme.''



``I think I speak for everyone when I say we just lost what little respect we had for you,'' Tattletale quipped.



Leet lunged for the two of them.  He didn't get three steps before Regent made him stumble and fall to his hands and knees.  The sword slipped from his grasp and slid over the pavement before flickering out of existence.



He was only a few feet from me, too focused on Tattletale and Regent to pay enough attention to me.  I reached behind my back, withdrew my baton and snapped it out to its full length.  As he started climbing to his feet, reaching behind his back for what I realized was a thin, hard backpack, I swatted at his hand with the length of metal.  He yelped, pulling his hand to his chest to cradle it.  I hit him in the calf, just below the knee, a little harder than I'd intended to.  He crumpled.



Stepping around him, I grabbed the end of the baton with my other hand and pulled the length of metal hard against his throat.



Leet started to make strained choking noises.  He caught me off guard by bucking backward, throwing the two of us onto our backs, him on top of me.  I winced as the impact brought his weight against the bruised area of my chest where Glory Girl had thrown Tattletale at me.  I didn't lose my grip, though.  Ignoring the one hundred and thirty pounds on top of me, I was glad for the extra leverage being on the ground afforded me.



``You okay?'' Grue asked me in his echoing voice.  He stepped forward so he was standing over me.



``Peachy,'' I replied, huffing with the exertion.



``Don't pull it against his windpipe.  You'll get tired enough that you lose your grip before he ever passes out.  Here,'' he bent down and forced Leet's head to one side, moving the baton so it was pressing against the side of Leet's neck, ``Now you're pulling against the artery, obstructing the blood flow to his brain.  Twice as fast.  If you could put pressure on both arteries, he'd be out in thirty seconds.''



``Thanks,'' I huffed, ``For the lesson.''



``Good girl.  \"{U}ber's down for the count, but I'm going to go help the others make sure he's not going to give us any more trouble.  We're only steps away, so shout if you need a hand.''



It wasn't fast, even with the technique Grue had instructed.  It wasn't pretty either.  Leet made lots of ugly little sounds, fumbling awkwardly for his backpack.  I pressed my body tight against it, though, and he gave up.  Instead, he tried pressing against the bar, to alleviate the pressure.  When that didn't work, he started scratching uselessly at my mask.



I released him when he finally slumped over.  Extricating myself from underneath him, I adjusted my mask, drew my knife and cut the high tech backpack off him.  When I'd done that, I searched him.  If we were going to interrogate him, it wouldn't do to have him digging out some little trinket to free himself or incapacitate us.  His costume was skintight, so it was easy enough to verify there weren't any hidden pockets or devices on him.  Just to be safe, I cut the antenna off his head and removed his belt.



The others returned with a battered and unconscious \"{U}ber in their arms, his arms bound behind him with plastic wrist ties.  They dumped him beside Leet.



``Now to find out where they stashed Bitch and the cash,'' Tattletale said.  She looked at me, ``Got any smelling salts?''



I shook my head, ``No.  These guys have henchmen, don't they?  They've probably got them watching over the money.  We'd likely find Bitch in the same place.''



``Close but no cigar,'' a mechanical hiss answered me.



We wheeled around to see a woman in the same outfit \"{U}ber and Leet were wearing.  The difference was that she wore a gas-mask style fixture over her lower face, and the lenses of her goggles were red, not black.



The woman's mask seemed to take what she said and replay everything in a robotic, monotone hiss, ``I really hoped they would take one or two of you out of the picture, or at least injure someone.  How disappointing.  They didn't even get around to introducing their guest star for tonight.''



``Bakuda?'' Tattletale was the first to put a name to the face, ``Fuck me, the game their costumes were from\ldots Bomberman?''



Bakuda stood and bowed in one smooth motion.  Regent raised his hands, but she let herself drop to her knees, gripping the roof's edge with one hand to avoid sliding off.



``Nuh uh uh,'' she waggled one finger at him, ``I'm smart enough to learn from the mistakes of others.''



``You seriously left the ABB to join \"{U}ber and Leet?'' Regent asked, astounded.



``Not exactly,'' Bakuda said.  She snapped the fingers of the hand she wasn't using to keep hold of the roof.



Below her, the door to the storage locker opened.  Three men in ABB colors stepped out, each holding a weapon.  A gun, a baseball bat, a fire axe.



Then other doors opened, all down the corridor of storage lockers.  Thirty or forty doors, each with at least one person behind them.  Some with three or four.  All of them armed.



``Those two were cheap hires.  They just wanted a few hundred dollars and I had to wear this costume.  Guess you get what you pay for.



``Goes without saying, I'm still with the ABB,'' Bakuda stated the obvious for us.  ``In charge, matter of fact.  I think it's fitting that I commemorate my new position by dealing with the people that brought down my predecessor, don't you agree?''



She didn't expect an answer, nor did she wait for one.  She pointed at us and shouted, ``Get them!''





