





Grue raised his hands and blanketed the entire area in darkness.  It wouldn't help much.  Even if they hesitated or got confused in the darkness, the crush of bodies would eventually stumble into us, and we'd be beaten and battered under the sheer force of numbers.  The only real advantage was that if any of them had guns, they probably wouldn't shoot, for fear of hitting their own guys.



I felt hands seize my waist, and lashed out with my baton.  The hands let go, and the baton hit only air.  After a moment, I felt the hands grab me again, the hold gentle.  Not an enemy.  Grue, I realized.



``Sorry,'' I muttered.  He could hear inside his darkness, couldn't he?



He hoisted me up into the air, and I immediately understood his intent.  I reached up and felt brick, then found the corrugated metal of the roof.  I hauled myself up and turned around to reach for the next person, one hand gripping the edge of the roof to keep myself in place.



I found Regent and Tattletale's hands in the darkness and helped haul them up.  I knew neither was Grue, because they were too light.  Five or six seconds long, tense seconds then passed before Grue took my hand and hauled himself up.



We climbed down the far side, and Grue banished the darkness around us.



There were three ABB gang members standing at one end of the alley we'd just entered, and a fourth, lone member on the other.  Both groups were looking the wrong way, and were standing still, which was as good an indication as any that they hadn't noticed us.



The sheer number of soldiers we'd seen didn't fit, and I said as much,  ``What the fuck?  How many people was that?''



Grue was apparently thinking along the same lines. ``The ABB shouldn't have that many members.''



``They do now,'' Tattletale glanced over her shoulder at the ABB members behind us, then back to the lone one in front who still hadn't reacted to our approach, ``Trap!  Down!''



She practically shoved me to the ground, then took cover herself.



The lone figure in front of us shimmered, then disappeared.  In his place, for just a fraction of a second, there was a cylindrical object the size of a mailbox.  Knowing what kind of devices Bakuda specialized in, I drew my legs close to my body, screwed my eyes shut and covered my ears.



The force of the explosion hit me hard enough I could feel it in my bones.  It  lifted me clear off the ground.  For a moment, it felt like I was floating, carried by a powerful, hot wind.  I hit the ground with my elbows and knees first, and they thrummed with agony at the impact.



Chaos.  The four or five storage lockers that had been closest to the canister had been  reduced to chunks of flaming brick, none any bigger around than a beachball.  Other lockers near those had doors, walls and roofs blown away.  More than one locker had been actually used, because the blast had emptied them of its contents.  Pieces of furniture, boxes of books, clothing, bundles of newspaper and boxes of papers filled the alley.



``Everyone okay?'' Grue asked, as he staggered to his feet.



``Ow.  I'm burnt.  Fuck!  She was expecting us,'' Tattletale groaned.  However bad her burns were, they weren't severe enough to be seen through the smoke and dust. ``Set traps, had her people waiting.  Shit, we were only a half hour later than we planned.  How?''



``We have to move,'' Grue urged us, ``This gets ten times harder if she finds us.  Tattletale, watch for-''



``I already found you,'' Bakuda called out in what could have been a sing-song voice, if her mask didn't filter it down to a monotone, rythmless hiss.  She emerged from the smoke that billowed from the explosion site; her hood was pulled back and her straight black hair was blowing in the wind.  The lenses of her dark red goggles were almost the exact same color as the sky above her.  There were five or six thugs just a step or two behind her, a middle aged guy that didn't look like a gang member, and a skinny boy who was probably younger than me.  I was glad to see none of them had guns, but they were all armed with weapons of some sort.



``Not that you were hard to find,'' Bakuda continued, sweeping her arms out to gesture at the devastation all around her.  ``And if you think this only gets ten times harde-''



Grue blasted her, shutting her up, and his darkness billowed into a broad cloud as it struck her, enveloping her group.  We took advantage of their momentary blindness to scramble for the other end of the alley.



We were only halfway down the length of the alley when there was a sound behind us, like the crack of a whip.  It struck me as deeply wrong, since we shouldn't have been able to hear \emph{anything} through Grue's darkness.  All at once, it was like we were running against a powerful headwind.



Except it wasn't wind.  As I looked for the source of the noise, I saw Grue's cloud of darkness shrinking.  Debris began to slide towards the epicenter of the darkness, and the wind – the pull – began to increase in intensity.



``Grab something!'' Grue bellowed.



Breaking posture and lunging to one side was like forcing myself to leap over a hundred foot chasm.  I don't know if I misjudged, or if the effect that was pulling on me increased in strength as I leaped, but my hand fell short of the doorknob.  I missed the one on the neighboring locker as well.



I knew in an instant that even if I managed to get my hand on something, the force of the pull would yank me from it before I secured a grip.  I grabbed my knife from its sheath at the small of my back and swung it with all the strength I could spare for the next door I saw.  It bit into the wood, stopping me from being dragged backwards, or falling sideways.  The one-hundred and twenty pound body hanging off of it was too much, though, and almost immediately, the knife began to slip from the hole.



It had slowed me down enough, though.  As the force of the drag increased to the point that my body was parallel to the ground, I waited with my heart in my throat, watching the area where the knife met the door, seeing it slide out millimeter by millimeter.  The moment it slipped free of the wood, I grabbed the doorknob that had been just a few feet beside my toes.  My arm jolted painfully, but I managed to hold on and jam the knife into the gap between the door and the frame.  Even with two things to hold onto, it didn't feel like enough.



All at once, the effect stopped.  My body collapsed to the ground at the base of the locker, and I pried stiff fingers from the knife handle and knob.  All up and down the street, massive clouds of dust rolled towards the point her device had gone off.  The parts of the lockers that had been set on fire had been extinguished, but were still smouldering enough to send columns of dark smoke into the air.



Regent had found a grip on the edge of a locker's roof; it had either been bent prior to his getting a grip on it, or the force of the pull had bent the metal as he clung to it.  Tattletale and Grue had apparently gotten a door of a locker open, because they exited as a pair, Grue limping slightly.



``What the fuck was that?'' I panted, ``A miniature black hole?''



Tattletale chuckled, ``Guess so.  That was brac-''



From the other side of the storage lockers, a canister arced through the air, clinked off the metal roof of a storage locker and landed in the middle of our group.



Grue was on it in a heartbeat, using his foot to slide it across the ground and into the locker he and Tattletale had just left.  Without stopping, he opened his arms wide and ushered us all away as he ran away from it.



Even with brick and concrete in the way, the blast knocked us off our feet.  That wasn't the scary part.  As the initial blast passed, the remainder of the explosion seemed to happen in slow motion.  Shattered chunks of the brick shack drifted through the air so slowly you could barely tell they were moving.  As I watched, I could see them actually slowing down.



Then I looked forward and saw plumes of smoke in fast motion and rubble bouncing across the ground at twice the normal speed, just ten feet ahead of us.  It took me a precious second  to realize why.



We were still in the blast area.



``Hurry!'' I shouted, at the same moment that Tattletale yelled, ``Go!''



We lunged forward, but I could see things continuing to speed up just in front of us.  Which meant, really, that we were slowing down.  Slowing to an absolute stop.



Somehow, I didn't think this effect would end in a matter of minutes like Clockblocker's did.



We broke through the perimeter of the effect with what felt like an abrupt change in air pressure.  I didn't have a chance to check to see how close we'd come to being trapped in time forever, because Bakuda was behind the row of locker, launching another salvo – three projectiles that arced high into the air, plumes of purple smoke trailing behind them.



Grue shot blasts of darkness at them, probably in hopes of muffling the effects, and gasped, ``Over the lockers!''



Regent and I were up on the row of lockers first, much the same way as we'd done it when the mob had been after us.  Once Regent had climbed down to make room, Tattletale and I helped Grue up, and we climbed down the far side.



Again, on each end of the alleyway, there were members of the ABB.  They weren't moving, which meant they either hadn't noticed us, or they were just holographic images hiding traps.  My money was on the latter.



``Again,'' I panted, ``Over.''  We couldn't risk another trap, another bomb blast too close to us.  So we crossed the alley again and climbed on top of the next row of lockers.



We found ourselves staring down at a half dozen armed members of the ABB.  Except they weren't your typical gang members.  One of them was an elderly Chinese man, holding a hunting rifle.  There was an girl who couldn't have been much older than twelve, holding a knife, who might have been his granddaughter.  Of the eleven or twelve of them, only three had the thuggish look to them that really marked them as members of the gang.  The rest just looked terrified.



The old man trained his gun on us, hesitated.



A thug with a tattoo on his neck spat out something in an Eastern language I couldn't place, the phrase ending with a very English, ``Shoot!''



We were down off the other side of the lockers before he could make up his mind.  Grue created a cloud of darkness over the top of the lockers, to discourage them from following.



``What the fuck?'' Regent gasped.  We hadn't stopped running or struggling since Bakuda had sicced the crowd on us.



``They're scared, not loyal,'' Tattletale spoke, not as out of breath as Regent, but still definitely feeling the effect of the last few minutes of running and climbing, ``She's forcing them to serve as her soldiers.  Threatening them or their families, probably.''



``Then she's been working on that for some time,'' Grue said.



``Since Lung got arrested,'' Tattletale confirmed, ``Where the fuck do we go?''



``Back over the same wall,'' Grue decided.  ``I'll blind them, we cross over at a different point in case they open fire where they last saw us.''



Before we could put the plan into motion, there was another explosion. We staggered into the front wall of the storage locker we'd just climbed down from, collapsing in a heap.  My entire body felt hot, and my ears were ringing, and we hadn't even been that close.



As I raised my head, I saw that one of the storage lockers across from us had been leveled.  Through the gap, I saw Bakuda standing astride the back of a jeep, one hand gripping the roll cage that arced over top of the vehicle.  She was saying something to the thugs in the front and passenger seats, but I couldn't make it out over the feedback noise in my ears.  They peeled off to the right, and for just a fraction of a second, she looked at me.



I reached for my bugs and directed them towards her, but she was moving too fast.  That left me the option of spreading them out so they were in her way, in the hopes that she would run straight into them, and maybe enough would survive the bug-against-a-windshield impact to give me a sense of where she was.



``She's going around,'' I said, grabbing at Tattletale's wrist, ``We can't go over the wall.''



``We gotta keep running,'' Regent panted.  I was having trouble hearing him.



``No,'' Grue stopped him, ``That's what she wants.  She's herding us into the next trap.''



``Where do we go, then?'' Regent asked, impatient, ``Fight her head on?  Catch her by surprise?  If I can see her, I can mess with her aim.''



``No.  She's got enough raw firepower to kill us even if she misses,'' Grue shook his head, ``We don't have many options.  We go over this wall again, we won't just have to deal with the thugs and the old man.  We go down either end of this alley, we're walking face first into a bomb.  So we have to backtrack.  No choice.''



I wished there was another option.  Backtracking meant moving back toward the center of the facility, it meant prolonging our escape, and possibly running headlong into ABB troops.



We headed for the gap that Bakuda's latest explosion had created in the lockers, and Grue filled the alley we were leaving with darkness, to help cover our escape.  The little road was empty, except for the still figures at either end.



As we started to climb over the next row of lockers, we felt rather than heard a series of explosions rip through the area behind us.  Bakuda was bombarding the cloud of darkness with a series of explosives.  I guess you didn't need to see if you could hit that hard.



We climbed down from the lockers and found ourselves in the same place we'd been when we escaped the mob.  There were three still figures at one end of the alley, doubtlessly a concealed bomb, and the destruction caused by the explosions and the miniature black hole in a can on the other.  If we climbed over the locker, we faced the risk of throwing ourselves straight into the mob we'd fled.  We'd have the element of surprise, but we'd be outnumbered, and our firepower was virtually nil.



By unspoken agreement, we headed towards the end of the alley where the hologram-bomb had gone off, where plumes of dust were still settling.



We were greeted by the sound of guns being cocked.



My heart sank.  Twenty or so members of the ABB had guns of various sorts trained on us.  Kneeling, sitting and crouching in front of the two groups, so they were out of the way of the guns and out of sight, were thirty or so other people Bakuda had `recruited'.  There was a businessman and a woman that could have been his wife, a girl wearing the Immaculata school uniform, from the Christian private school in the south end of the city, about my age.  There were two older men, three older women with graying hair, and a group of guys and girls that might have been University students were standing together.  Everyday people.



They weren't gang members, but I could think of them as her soldiers; Every one of them held a weapon of some sort.  There were kitchen knives, baseball bats, pipes, shovels, two-by-fours, chains, crowbars and one guy even had a sword that was, oddly enough, not Japanese.  There was a look of grim resignation on their faces, circles under their eyes that spoke of exhaustion, as they watched us.



Behind their assembled group, standing astride the Jeep, one foot resting on her modified jeep-mounted mortar launcher, an altered grenade launcher danging from one strap around her shoulders, was Bakuda.  All around her were boxes of her specialized grenades and mortar rounds, bolted onto the back of the Jeep, blinking with various colored LEDs.



She put her hands on her grenade launcher as she tilted her head to one side.  Her robotic voice crackled through the still air.



``Checkmate.''





