





I'd discovered facing down more than a dozen gunmen, thirty or so people with improvised weapons and a mad scientist with a fetish for bombs made me really, really appreciate what Bitch brought to the team.



``All of this,'' Tattletale spoke very carefully, ``You were toying with us.  It's why you didn't have your people shoot at us from the start.''



``You're very right.'' Bakuda's mask may have altered her voice to something approximating Robbie the Robot with a sore throat, but I got the impression she tried to make up for it with body language.  She shook her finger at Tattletale like she was scolding a dog.  ``But I think you, specifically, should shut up.  Boys?''



She rested her hand on the head of an ABB member standing in front of her jeep with a pistol in his hands.  He flinched at the touch.  ``If the blonde opens her mouth again, open fire on their entire group.  I don't care what the others have to say, but she stays quiet.''



Her soldiers adjusted their grips on their guns, and more than one turned the barrel of their weapons to point towards Tattletale, specifically.  Glancing at Tattletale, I saw her eyes narrow, her lips press together in a hard line.



``Yeah,'' Bakuda straightened up, put a foot up on the top of the Jeep's door and rested her arms on her knee, leaning towards us. ``You're the only one I don't get.  Don't know your powers.  But seeing how you and the skinny boy baited my ineffectual mercenaries, I think I'm going to play it safe and have you be quiet.  Maybe it's a subsonic thing, altering moods as you talk, maybe it's something else.  I dunno.  But you shut up, `Kay?''



Out of the corner of my eye, I could see Tattletale give the slightest nod.



``Now, I'm in a bit of a pickle,'' Bakuda hissed, examining the back of her hand.  It seemed she wasn't just compensating for the mechanical voice with body language; she liked to talk.  Not that I was complaining.  ``See, Lung taught me a lot, but the lesson I really took to heart was that being an effective leader is all about \emph{fear.}  Career like ours, people are only truly loyal to someone if they are terrified of them.  Enough fear, and they stop worrying about their own interests, stop wondering if they can usurp you, and they dedicate themselves entirely to making you happy.  Or at least, to keeping you from being unhappy.''



She hopped down from the jeep and grabbed the hair of a taller, longer haired Japanese guy from a group of twenty-somethings.  Winding his hair in her hands, she made him bend over until his ear was right in front of her, ``Isn't that right?''



He mumbled a reply and she released him, ``But it goes further, doesn't it?  See, I may have inherited the ABB-''



It was almost imperceptible, but I saw a flicker of movement around Tattletale's face.  A change of expression or a movement of her head.  When I glanced her way, though, I couldn't guess what it had been.



Bakuda continued without a pause, ``But I also inherited Lung's enemies.  So I have a dilemma, you see.  What can I do to you that's going to convince them that I'm worth steering clear of?  What gesture would be effective enough that it would have their people running for the hills when they see me coming?''



She wheeled around and grabbed a pistol from the hands of one of her thugs, ``Give.''



She then strode forward into the midst of the crowd.



``There's not enough bugs here.'' I took advantage of the pause in her monologue to whisper under my breath, hoping the others would catch it, praying I wasn't being too loud.  At least my mask covered my face, hid the fact that my lips were moving, ``Regent?''



``Can't disarm this many guns,'' he whispered his reply. ``I mean, I-''



``You.'' Bakuda called out, startling us.  She wasn't paying attention to us, though.  A Korean-American guy in a private school uniform – from Immaculata High, in the nicest part of the city – was cringing in front of her.  The crowd slowly backed away, clearing a few feet of space around the two of them.



``Y-yes?'' the boy replied.



``Park Jihoo, yes?  Ever hold a gun before?''



``No.''



``Ever beat someone up?''



``Please, I never\ldots no.''



``Ever get in a fight?  I mean a real fight, biting, scratching, reaching for the nearest thing you could use as a weapon?''



``N-no, Bakuda.''



``Then you're perfect for my little demonstration.''  Bakuda pressed the pistol into his hands, ``Shoot one of them.''



The guy held the gun like it was a live scorpion, with two fingers, at arm's length, ``Please, I can't.''



``I'll make it easy for you,'' Bakuda might have been trying to coo or sound reassuring, but mask didn't allow for that kind of inflection, ``You don't even have to kill them.  You can aim for a kneecap, an elbow, a shoulder.  Okay?  Wait a second.''



She left the gun in the guy's hands and stepped away, pointing to one of her thugs, ``Get the camera out and start rolling.''



As ordered, he reached for the side of the jeep and retrieved a small handheld camcorder.  He fumbled with it for a few seconds before holding it over his head to see past the crowd,  looking through the flip-out panel on the side to make sure the camera was on target.



``Thank you for waiting, Park Jihoo,'' Bakuda turned her attention to the guy with the gun, ``You can shoot someone now.''



The guy said something in Korean.  It might have been a prayer, ``Please.  No.''



``Really?  They're bad people, if you're concerned about morals.''  Bakuda tilted her head to one side.



He blinked back tears, staring up at the sky.  The gun fell from his hands to clatter to the pavement.



``That's a no.  Shame.  No use to me as a soldier.''  Bakuda kicked him in the stomach, hard enough to send him sprawling onto his back.



``No!  No no no!'' The guy looked up to her, ``Please!''



Bakuda half-stepped, half skipped back a few feet.  The people around them took that as their cue to get well away from him.



She didn't do anything, didn't say anything, didn't offer any tell or signal.  There was a sound, like a vibrating cell phone on a table, and Park Jihoo liquefied into a soupy mess in the span of a second.



Dead.  He'd died, just like that.



It was hard to hear over the screaming, the wailing, the outraged shouts.  As the crowd scrambled to back away from the scene, all trying to hide behind one another, one of the thugs fired a gun straight up into the air.  Everyone stopped.  After the shrieks of surprise, there was the briefest pause, long enough for one sound to bring everyone to a stunned silence.



It sounded like the noise you make when you rake up dry leaves, but louder, artificial in a way that sounded like it was played over an archaic answering machine.  All eyes turned to Bakuda.  She was doubled over, her hands around her middle.



Laughing.  The sound was her laughing.



She slapped her leg as she stood, made a noise that might have been an intake of breath or a chuckle, but her mask didn't translate it into anything recognizable – only a hiss with barely any variation to it.  She spun in a half circle as she crowed, ``The six-eighteen!  I forgot I even made that one!  Perfect!  Better than I thought!''



If her job was to terrify, she'd succeeded.  With me, at least.  I wanted to throw up, but I'd have to take off my mask to do it, and I was afraid that if I moved, I'd get shot.  The fear of the guns was enough to override my welling nausea, but the end result was that I was shaking.  Not just trembling, but full body shakes that had me struggling to keep upright.



``That was pretty cool.''



With those words, Regent managed to get as many wide eyed looks than Bakuda had with her laugh.  He got one from me.  It wasn't just what he said.  It was how calm he sounded.



``I know, right?'' Bakuda turned around to face him, cocked her head to one side, ``I modeled it off Tesla's work in vibrations.  He theorized that if you could get the right frequency, you could shatter the Earth it-''



``No offense,'' Regent said, ``Well, I'll rephrase: I don't really care about offending you.  Don't shoot me though.  I just want to stop you there and say I don't care about the science stuff and all the technobabble about how you did it.  It's boring.  I'm just saying it's kind of neat to see what a person looks like when dissolved down like that.  Gross, creepy, fucked up, but it's neat.''



``Yes,'' Bakuda exulted in the attention, ``Like the answer to a question you didn't know you were asking!''



``How'd you do it?  You stuck bombs in these civilians to get them to work for you?''



``Everyone,'' Bakuda answered, almost delirious on the high of her successful `experiment' and Regent's attention.  She half skipped, half spun through the crowd and leaned against one of her thugs, patting his cheek, ``Even my most loyal.  Bitch of a thing to do.  Not the actual procedure of sticking the things inside their heads.  After the first twenty, I could do the surgeries with my eyes closed.  Literally.  I actually did a few that way.''



She pouted, ``But having to tranquilize the first dozen or so and do the surgeries on them before they woke up, so I'd have the manpower to round up everyone else?  One after the other?  Really tedious once the novelty wears off.''



``I'd be too lazy to do that, even if I had your powers,'' Regent said, ``Can I approach the body?  Get a better look?''



Her mood changed in a flash, and she angrily jabbed a finger in his direction. ``No.  Don't think I don't know you're trying something.  I'm a fucking genius, get it?  I can think twelve moves ahead before you've even decided on your first.  It's why you're standing there and I\ldots'' she hoisted herself up so she was sitting on the side of the Jeep, ``Am sitting here.''



``Chill the fuck out,'' Regent replied, ``I was just asking.''



I could see from Tattletale's expression that she was having the same thoughts I was.  \emph{Give the lunatic bomber a little respect.}  I quietly voiced what Tattletale couldn't.



``Tone it down a notch, Regent,'' I whispered.



``Whaaattever,'' Bakuda drew out the word, ``Skinny boy just lost any goodwill he'd earned for appreciating my art.  Or at least being able to fake it convincingly.''  She tapped the guy with the camera on the shoulder, ``You still filming?''



The man gave a short nod.  As I looked at him, I saw beads of sweat running down his face, even though it was a cool evening.  It seemed her thugs were pretty spooked, too.



``Good,'' Bakuda rubbed her pink-gloved hands together, ``We'll edit out the talky parts later, then we put it on the web and send copies to local news stations.  What do you think?''



The camera-guy answered in an accented voice, ``Good plan, Bakuda.''



She clapped her hands together.  Then she pointed into the crowd  ``Alright!  So, you\ldots  yeah you, the girl in the yellow shirt and jeans.  If I told you to, would you pick up the gun and shoot someone?''



It took me a second to spot the girl, at the far end of the crowd.  She looked at Bakuda with a stricken expression and managed to answer, ``The gun m-melted too, Ma'am.''



``You call me Bakuda.  You know that.  Nothing fancy.  If the gun was still there, would you shoot?  Or if I told someone to give you a gun?''



``I-I think I maybe could,'' her eyes flickered to the puddle that had been Park Jihoo.



``Which concludes my demonstration,'' Bakuda addressed our group, ``Fear!  It's why Lung went out of his way to recruit me.  I always understood deep down inside, that fear was a powerful tool.  He just phrased it so well.  True fear is a blend of certainty and the unpredictable.  My people know that if they cross me, I only have to think about it to make the bombs in their heads go kablooie.  Boom.  They know that if I die, every single bomb I've made goes off.  Not just the ones I jammed into their heads.  Every single fucking one.  And I've made a lot.  Certainties.''



Lisa reached out and grabbed my hand, clenched it tight.



``As for unpredictability?''  Bakuda kicked her legs against the side of the jeep like a grade schooler sitting on a chair, ``I like to mix up my arsenal, so you never know what you're going to get.  But you've also got to keep your people wondering, right?  Keep them on their toes?  Case in point: Shazam!''



The word coincided with the start of a very real explosion that was closely followed by something like thunder, but Lisa was already pulling on my arm, pulling me away.



I saw a glimpse of chaos, of screaming people running from the place the explosion had happened in the midst of Bakuda's own group.  The fleeing people were obstructing the view of the people with guns.



Regent stuck his arm out, swept it outward, sending ten or so people stumbling into one another, turning the crowd into a disordered mob.  I heard the too-loud roar of guns being fired, saw Regent grab the shoulder of a limp left arm, couldn't be sure the two were connected.



Finally, there was Bakuda, still sitting on the side of the jeep.  She was either shouting something or laughing.  She was letting us slip from her grasp, her people were on the verge of killing one another in mindless panic, and she'd just killed at least one of her own people on a whim.  From what we'd just seen of her, I was willing to bet she was laughing as it all happened.



Almost without my noticing, night had fallen, and as if to invite us deeper into the maze, the light poles flickered and turned on above us.  With Grue covering our retreat in a curtain of darkness, we ran.





