





``Did you get shot?'' I asked Regent, as the four of us dashed down the alleyway.  No answer.  So I tried again, more specific, ``Regent!  Listen to me, did you get shot?''



He shook his head in a tight motion as he clutched his hand against his shoulder, ``Not shot.  Used my power too much, too fast, and it backfired.  Left arm's cramping up, spasms.  I can't move it.  Don't worry about it.''



``Backfired?'' I asked.



``Don't worry about it!'' his snarled response was all the more startling because it came from our normally placid and too-laid-back Alec.  As if to compensate for the lashing out, he muttered an apology, ``Fuck.  Sorry.  This hurts, but I'll deal.  You guys focus on getting us out of this mess.''



``Tattletale,'' I was still holding her hand, so I squeezed it to ensure I had her attention, ``This would be a fantastic time to do your thing.''



``Especially since you dropped the ball as far as letting us walk into that fucked up situation,'' Grue growled.



``Okay,'' Tattletale huffed with both the exertion of our run and her irritation, letting go of my hand to push her hair back from her face and put it behind her ears, ``The big one: She's lying.''



``About?'' I asked.



``She's not the new leader of the ABB.''



``What?  Who is?'' Grue asked.



``Your guess is as good as mine.  She doesn't see herself as the one in charge, as much as she enjoys the role.  She's pretending.''



The ground rumbled, and we looked behind us to see debris spraying out of the darkness Grue had used to cover our retreat.



It was only because we were watching the debris that we saw the rocket blast out of the darkness.  We ducked, needlessly, as the missile arced 3 feet over our heads and continued down the alley, directly to the spot where a hologram-bomb sat.



We covered our heads as the rocket and bomb exploded, one just a second after the other.  The first explosion didn't even ruffle our hair, though we were less than a hundred feet away.  The second, explosion, though, ripped past us with the most intense cold I'd ever felt.  Even through my costume, I could feel it.



When we opened our eyes, there was a spectacle in front of us.  The second explosion had flash-frozen the first bomb mid-explosion, had probably been what absorbed the force of the blast.  Smoke, debris and dust had been frozen into a tower of ice, easily as tall as a two story building, composed of spikes of ice and frost that radiated up and away from us.  Most of it was lit up by the lightposts that were spaced evenly across the storage facility.  It was already slowly falling apart – heavier pieces of debris were breaking through the ice that held them up, falling free and crashing through paper thin latticeworks of frost.



That same frost covered the ground and every wall that was facing the explosion site, as far as the eye could see.  It covered \emph{us}.  Icicles so tiny and fine they were like eyelashes radiated from the parts of my costume that had been exposed.  There were even twists and curls of ice where Grue's smoke had frozen.



``Everyone okay?'' Grue asked.  He was shielding Tattletale with his body, the ice sloughing off them in sheets as they stood.  When he saw me looking, he explained, ``Tattletale's costume exposes her skin, more than any of us.  If she'd been totally exposed-''



``No,'' I answered, ``No worries.  Smart.  But we should move.''



We ran.  All around us, tiny crystals of ice were drifting down, sparkling in the light.



Tattletale continued dishing the info on Bakuda, ``Lie number two?  She's fibbing about how she's detonating those bombs she has in her people's heads.  She said she blows things up with a thought, but she's not wearing any external hardware on her head, and she's  wouldn't have someone else do surgery on her.  Too much of a control freak, too proud of her brain.''



``But you don't know how she's blowing the bombs up?'' I guessed.



``I know exactly how she's setting them off.  Toe rings.''



``Toe rings,'' Grue said, disbelief clear in his tone, even with his warped voice.



``She's got a ring around her big toe and the toe next to it.  When she crosses one toe over the other, contacts on the outside of the rings meet and it sends the signal.  She chooses the target with a system built into her goggles.  It doesn't \emph{look} like she's doing anything, which is probably the effect she's going for.  Appearances.''



``Good to know,'' Grue said, ``But that doesn't help us right now.  What are her weaknesses?''



There was the crash of an explosion behind us.  The area briefly lit up, but it hadn't hit close enough to be worth worrying about.



``Narcissistic personality disorder.  Megalomania.  She's spent her whole life being smarter than everyone around her, even before she had powers.  Constantly praised, coddled.  But she rarely if ever heard a criticism, probably wasn't ever knocked down a peg, and that was a big factor in her ego swelling up to neurotic levels.  Probably graduated high school years early.  My bet is her trigger event was related to this.  Passed over for a job or someone really bitched her out, and she didn't know how to deal.''



I had something to add, ``The first thing she did with her powers, only thing, before she came to Brockton Bay, was hold a University hostage.  Maybe she got some bad marks, failed a class or was passed over for a teaching assistant position.  Jarred her self image enough she snapped.''



``Something we can use, people!'' Grue growled.



``The personality disorder,'' Tattletale said, ``Even a small victory on our end is going to get a big reaction from her.  Ego-wise, she's got a glass jaw.  Hard to say if a win for us would mean she goes manic and blows everything up, or if she'd just crumple, but I guarantee she wouldn't handle it well.''



Grue nodded, started to speak, but stumbled.  I did my best to stop him from falling over, but he probably weighed half again as much as I did.  He got his balance, growled, and then spoke, ``How do we win?  Or how do we avoid losing?  What's she got going on that we don't know about?''



``The goggles.  She's seeing heat signatures.  It's how she kept finding us.  That ice is a blessing in disguise, since it's probably hiding us some.  She must have a reason for using it.  Um.  Her guns are keyed to her fingerprints, so you couldn't pick up her grenade launcher and use it against her.''



``What else?''



``That's all that's coming to mind right now.  If you're going to come up with a plan, best do it fast.  I think she's after us on the Jeep.''



``Then we're splitting up,'' Grue grunted, ``I fucked up my ankle by kicking in that door when the black hole hit.  I fucked it up worse by running so much afterward.  I'm going to see what I can do, staying here.''



``What the fuck?'' I breathed, ``No.''



``I'll buy you time.  You guys go.  Now!''



``No way,'' I said, but he was stopping, turning around.  I tried to stop, too, but Tattletale took hold of my hand and dragged me after her.  I shouted, ``Grue!  Don't be stupid!''



He didn't respond, turning to fire blasts of darkness at the lights nearest him, darkening the entire alley.  Slowly, he walked in the opposite direction the rest of us were going, favoring one leg.



With a whistle and a resounding crack, another rocket slammed into the tower of ice.  The entire thing toppled like a massive house of cards, with a sound of a hundred thousand windows breaking.  Even with that cacophony, I heard the squeal of tires.  I saw the blurred form of the Jeep approaching through the cloud of snow and frost that was rolling away from the collapsed tower.



Grue didn't retreat as the Jeep barreled forward, didn't turn away.  He bellowed at the top of his lungs, in his altered voice, ``Come on!''



``Grue!'' I shouted, but he didn't react.  ``Fuck!''



No bugs.  Still too few.  We'd been constantly moving, so my bugs hadn't had a place they could congregate, and this place was lousy for them anyways, in quality and quantity.  How could I have been so goddamn stupid?  I should \emph{always} be prepared, and now I wasn't in a state to help a friend and teammate when he needed it most, because I'd assumed my bugs would be on hand.



There were only three people in the Jeep, with the person standing at the back being the very recognizable Bakuda, grenade launcher in hand.  The thug in the passenger seat had a pistol in each hand, and the driver was steering with one hand, a gun in the other.



Grue didn't budge as the driver stepped on the gas.  Was he playing chicken against a speeding car?



``Come on!'' Grue shouted, again.



``Don't just watch!'' Tattletale tugged on my arm, pulling me toward the corner, ``We've gotta go now or there's no point!''



It was stupid, but I resisted, grabbing at the edge of the locker to ensure I could at least stay long enough to see what happened to Grue.  See if maybe he would be okay.



Those hopes were swiftly dashed.  The car slammed into the darkness-wreathed figure with enough speed to assure me he wouldn't be walking away from an impact.



The tires squealed and the Jeep skidded in a half-turn as it veered to a halt.  Bakuda pulled herself up to a standing position, holding on to the roll bar as she looked around, presumably for us.



``Come on!'' Tattletale urged me in a strained whisper, ``Let's go!''



I realized it before she did. ``There's no damage to the car.''



Tattletale's repeated yanking on my arm stopped as she paused to verify what I'd said.  No broken window, no dents on the hood, no dents on the bumper.



A cloud of darkness bloomed from the shadows at the side of the alley and swallowed the Jeep and its three occupants.



Two seconds later, the Jeep came roaring out of the darkness, fishtailing as the wheels struggled to get a grip on the frost-slick pavement.  The driver steered it towards us, while Bakuda loaded her grenade launcher, her focus on the cloud of darkness she'd just exited.  The guy in the passenger seat\ldots was gone.



Bakuda aimed the grenade launcher at the darkness.



``Fuck, Grue owes me one for this,'' Regent muttered.  He let go of his shoulder, raised his hand toward the Jeep, and then flung it out to one side.  As he did it, he screamed, his voice primal, raw.



The hand the driver had on the wheel moved much as Regent's did, swinging wildly to one side.  The Jeep turned, skidded, and spun out, flinging Bakuda and the contents of a half dozen boxes of explosives onto the road of the alley.  It collided with a locker, halfway smashing through a door in the process, and spiraled to a halt with a single airbag deployed, the driver limp behind it.



Almost at the same moment the Jeep stopped, Regent started to collapse to the ground, unconscious.  I grabbed him to stop him and eased him down so he didn't hit his head.  I looked at Tattletale, ``Backfire?''



``No, but close,'' Tattletale said, ``After a backfire, he's got to rest his powers.  It's like throwing a punch with a broken hand.  He'll be sore and probably powerless for a little while, but he'll recover.''



``Good,'' I said, staring out at the scene.  The crashed car, the frost-covered street covered with grenades and canisters, Bakuda lying still in the midst of it all.  Grue limped out of the cloud of darkness, the passenger's gun in his hand.



``Grue!'' I called out.  I ran to him, hugged him.  My relief was so intense I wasn't even embarrassed about it.



``Heya,'' his voice echoed, ``I'm alright.  Only a feint.  Hard to tell whether it's me or a blob of shadow shaped roughly like a person when the lights are out, yeah?  Fooled her.''



``Fooled me.  Scared the fucking crap out of me,'' I answered, ``You fucker.''



``Nice to know you care,'' he laughed a little, patted me on the head like someone would a dog, ``Come on.  We should restrain the lunatic, get her out of here so we can drill her on what happened to Bitch and the money.  Maybe get an idea of what's going on with the ABB.''



I smiled behind my mask, ``Sounds like a-''



I didn't get to finish.  Everything went white, then every inch of me bloomed in a searing agony that dwarfed the worst pain I had ever felt.



Since we had trounced \"{U}ber and Leet, it had been one close call after another.  Being surrounded and charged by a mob, being held at gunpoint, escaping a miniature black hole, nearly being frozen in time like bugs in amber, innumerable explosions.  We'd escaped each of the threats by the skin of our teeth, knowing all the while that all it would take was one well placed shot, and we were done, gone, out of commission.



All it had \emph{taken} was one good shot.





