





I came to the gradual realization I could open my eyes, as though it was something I had forgotten how to do.  I tried it and regretted my decision instantly.  One of my eyes wasn't seeing anything, even when open, and the other was out of focus, with images failing to make sense even when I could make something out.  As I screwed my eyes shut, even the pink glow of light passing through my eyelids was like fireworks exploding in my retinas.



When I tried to piece together what had just happened, my thoughts moved like molasses.



``If you little fucks had any sense, you'd know that getting the upper hand on me, just for a moment?  It's something you should be \emph{fucking terrified of},'' a voice hissed.  It took me a few seconds to place the voice, way longer than it should have.  Bakuda.



I was beginning to hurt.  Like papercuts, but blown up to two hundred times the size, and each of those papercuts was one of my muscles.  My skin was prickling with stings that were gradually feeling more and more like a burn.  My joints throbbed as though every single joint had been torn out of its individual socket and people were banging the still-alive ends of them against the pavement in a grim rhythm.



I opened my good eye again and tried unsuccessfully to focus.  Three crimson ribbons\ldots no.  I was seeing triple.  One crimson ribbon was extending along the side of my mask, dropping from the edge where the mask covered my nose, dropping in a straight line to touch the ground.  Where it made contact with pavement, there was a steadily growing puddle.  I realized I was bleeding.  A lot.



``Leaving me lying there with a grenade launcher in my hand and ammunition all over the fucking street was asking for it.  Fuck, just the hugging and being all relieved, as if you had \emph{actually} beaten me?  You were begging to be shot.''



I wasn't going out like this.  Not without a fight.  I could barely move, though, let alone take action.  My desire to do \emph{something} was almost more excruciating than the pain that throbbed and thrummed through my entire body.  What could I do?  My mind wasn't working as agonizingly slowly as it had been a moment before, but my thoughts were still bogged down and broken up.  Stuff I should have known without thinking about it was vague, uncertain, disjointed.  Too many thoughts were orphaned, disconnected from everything else.  I would have hit something in my frustration if I'd been able to move without everything hurting.  I settled for clenching my fists.



School.  Trouble at school?  Me?  The trio?  No.  Why was I thinking about school?  What had I been thinking about before I got frustrated?  Wanting to fight back somehow.  Bakuda, school, fighting back.  I almost groaned in frustration as I tried to connect the individual ideas, and simply couldn't complete the thought.  I only wound up huffing out a breath, wincing at the pain that caused.



``Oh?  The ineffectual little girl with the bug costume is awake,'' Bakuda's whirring voice announced to the night air.



Grue said something, a short distance away, I couldn't make it out.



Bakuda replied with an absent, ``Shush, don't worry.  I'll get to you in a moment.''



I heard something, and saw a pair of pink boots appear in front of my face, the image swimming and drifting lazily.



``Bad day?'' she bent over me, ``Good.  See, one of my new minions is on staff at the Protectorate Headquarters.  A guard where Lung is imprisoned, understand?  Wasn't in a position to free him, but she got the full story from him.  I know \emph{you} were the little freak that led to him getting sent there.  So \emph{you} get special treatment tonight.  You get to watch what I do to your friends.  I'll start with the boy in black, then move on to your unconscious buddies over there.  Glued them down just to be safe.  Once your friends are as good as dead, I give you to Oni Lee.  He was a very good boy when it came to the change of regime, and he's been bugging me to give him something to play with.  What do you say to that?''



I was only half listening.  Like a mantra, I was mentally reciting the same thing, over and over.  Bakuda, school, fight back.



``Bakuda, school,'' I mumbled.  Hearing how reedy and thin my own voice sounded was more terrifying than anything else that had come to my attention in the past few minutes.



``What?  Does the bug girl want to say something?''  She bent down and grabbed the armor that hung over my chest.  With a jerk, she hauled me into a half-sitting position.  Being tugged around like that was torture, but the pain helped sharpen my thoughts into a semblance of clarity.



``School.  Bakuda failed,'' I answered her, my voice only marginally stronger than it had been on my last attempt.  The black-red lenses of her goggles bored into me as I composed my thoughts to speak again, trying to sound more coherent. ``Smart as you think you are, failing like that?  What was it?  Second place?  Not even second?''  I managed something approximating a chuckle.



She let go of me and stepped away as if I was on fire.  As my head hit the pavement, I very nearly blacked out.  Had to fight not to.  \emph{Embrace the pain}.  \emph{Keeps you awake.}



A short distance from me, Grue's voice echoed.  I could only make out the first word.  ``She's'' or ``Cheese''.  He laughed.  It spooked me that I couldn't understand him, that I couldn't figure out \emph{why} I couldn't understand him.  I wasn't hearing as well as I should, I knew that.  But that wasn't all of it.  What else?



The distortion.  The explosion or explosions had damaged my hearing, maybe, and I couldn't make out his words with the effect his power had on his voice.  Just figuring that out, knowing I \emph{could} figure it out, made me feel a hundred times better.



``You think so?'' Bakuda hissed at Grue.  Her words were \emph{easier} to make out, since her mask was reconstructing them so they were perfectly enunciated and monotone, even if it obscured it behind whirs and hisses.



She kicked me in the face with one of those pink boots.  Having to move my head hurt more than almost having my teeth kicked in.  She grabbed at my costume and dragged me several feet.  Being moved cranked all the other hurt up a notch.  On a scale of one to ten, it was a good solid nine point five.  Nothing I could do could make it hurt more, so I found the strength and willpower to reach up and grab at her wrists, for all the good it did.  She let me go and then shoved me to turn me on my side.  The movement made me want to throw up.



Seeing Grue helped ground me, as I fought the nausea and panted tiny breaths at the pain.  He was bound in a half-sitting position against a locker with what looked like lengths of sticky gold ribbon.  Where was Tattletale?



``Let's see how smart you two are after I give tall, dark and mysterious his treat,'' Bakuda threatened, ``Let's see\ldots here.  Here's a real gem.  Two-twenty-seven.  Now sit still.  If you even think about using your power, I'll just shove it down the bug brat's throat instead, set it off.  Not like you're in a position to stop me from getting the job done, even if I'm deaf and blind.''



She removed her pink gloves and threw them aside.  Then she withdrew a set of what looked like long, narrow scissors from her sleeve.  Except they were blunt, not sharp.  Like pliers, almost.  They clicked as she closed them on the tip of what looked like an inch-long metal pill.



``No need for surgery, since this isn't going to be long term.  What I'm going to do is slide this up your nostril and into your nasal cavity.''  She reached into the darkness that was leaking from all around him and fumbled around his face. ``Just need to get your mask\ldots helmet\ldots off.  There.''



If Grue's mask was off, it was hard to tell.  His head was just a roughly human-shaped blur of shadow.



She reached into that layer of darkness with one hand and pushed the capsule into the center of it all with the other.  ``And in it goes\ldots slowly, don't want to activate it prematurely, and the effects will only be really cool if it's deep.  See, my two-twenty-seven was something of a happy accident.  I'd taken readings of little Vista's powers, thought maybe I could make a space distortion grenade.  Purely by accident, I cracked the Manton effect.  Or at least, whatever I'd done when I put the grenade together, it bypassed the Manton effect.  You idiots know what that is?''



She stopped and cracked her knuckles, leaving the scissor-like tool sticking straight out of Grue's face.  ``It's that little rule that keeps pyrokinetics from boiling your blood, that limits most powers from affecting people's bodies.  Or, depending on what theory you're going by, it's the rule that says your power either works only on organic, living things, or it works on everything else.



``So think about it.  A spatial distortion effect that only works on living material.  I set this thing off, and all living matter within three feet of the capsule is reshaped, warped, shrunk, blown up, stretched, bent.  It doesn't actually kill you.  That's the second most amazing thing about it, besides the Manton bypass.  Everything still connects to everything else.  Totally nonlethal, but it'll make you wish you were dead every second of the rest of your miserable fucking existence.''



\emph{Don't just lie there and watch}, I thought.  \emph{Do something!}



``Just click, whoosh, you're ugly enough to put the elephant man to shame.  Wind up with a head four times the normal size, bumps like tumors all over, every feature and part the wrong shape, wrong size.  Reshapes the brain, too, but that's usually just some mild to moderate brain damage, since I've got it calibrated to focus on the external features.''  She laughed.  It was that dry, repetitive, inhuman sound.  When she spoke again, she enunciated each word separately.  ``Irreversible.  And.  Fucking.  Hilarious.''



I reached for my bugs, but I couldn't draw my thoughts together enough to give them any complex commands.  I just called them to me.  That still left me to help Grue.



My utility sheath.  Slowly, as much due to my need to be discreet as to my inability to move very quickly without incredible pain, I moved my hand behind my back, reminded myself of what was there.



Pepper spray – no go.  It would burn her skin, but the goggles and mask would keep most of her face safe.  She was scraped and bloody, so maybe I could spray her body\ldots it wouldn't be fun on her wounds, but would that save us?



Pen and paper.  Cell phone.  Change.  No, no and no.



Baton.  I didn't have the strength to swing it, or the leverage or room I needed to extend it.



Epipens.  Not much use, and I didn't trust my strength or coordination as far as being able to both inject her \emph{and} depress the syringe.



That was it for the contents of my utility compartment.  I let my hand go limp and dangle behind my back as I braced myself to move it, and my fingers brushed against something.



The knife sheath at the small of my back.  I'd strapped it in at the lowest point it could be on my back, while being both covered by my armor and easy to reach.



Knife worked.



There was a faint click as Bakuda adjusted the scissor-plier things and removed them from Grue's nose.  They weren't gripping the capsule anymore.



``This should be a show,'' she gloated, standing up straight before I could figure out where to stab or cut.  Didn't want to kill, but had to stop her.  For Grue.



My hand was still behind my back, gripping the knife handle with the blade pointing out the bottom of my hand.  I shifted my position a fraction so my angle was better.



``Hey, bug girl.  What are you up to, there?  Flopping around like a fish on dry land?  Pay attention, it's going to look really cool when parts of his face start bulging out of that little blotch of shadow.''



I tried to formulate a response, some reply that would add sting to what I was about to do, but a wave of weakness swept over me.  Darkness began to creep in around the edges of my vision, again.  I straightened my legs in an attempt to cause myself more pain, force myself to alertness again, and it failed to push the darkness back.  Was Grue using his power?  I looked at him.  Nothing.  I was just blacking out.



I couldn't pass out now.



\emph{Toe Rings}.



With no witty reply, no quip or even an angry yell, I brought the knife down on the end of her foot.  Two thoughts struck me simultaneously.



I'd hit something hard.  Was her foot or boot armored?



Had I even gotten the right foot?  Tattletale had never said which one had the toe rings.  Or if both did.



As a wave of blackness swept in front of my vision and faded just as quickly, leaving me only dimly aware of her screams.  The nausea was welling again, and just like it was with my consciousness slipping away, the need to puke building.  I was going to throw up, but I could choke if I did it with my mask on.  If I wound up on my back, I could even suffocate.



Grue was saying something.  Couldn't make out his words.  Sounded urgent.



The woman was screaming in my ear.  A litany of curses, threats, horrible things she was going to do to me.  Unconsciousness called to me, seductive, safe, painless, free of threats.



If it was even unconsciousness. The chilling idea that I could be dying dawned on me, gave me the briefest moment of clarity.  I focused hard on the jumble of distorted images and sounds, where I was, what people were saying and screaming at me.



The woman was rolling on the ground next to me.  As she kicked her leg, a spatter of blood marred the one lens of my mask that I could see through.  What was the woman's name again?  Bakuda.  The very tip of the knife was still lodged in the pavement where her foot had been.  That was the hard thing I'd hit: pavement, not armor.  There was a lot of blood.  Hers.  A bit of her boot, pink and crimson.  Two smaller toes with painted nails, pink and crimson, in the midst of the mess of blood.



I tried and failed to pull the knife free, though it was only embedded a quarter-inch deep in the ground.  The effort that left me gasping for breath with big lungfuls of air.  Each breath made me feel like I'd inhaled barbed wire and hot irons were pressing against my sides.  I was praying the urge to vomit would go away, knowing it wouldn't.



Grue.  What was he saying?  I could barely understand Bakuda with her robotic enunciation.  Understanding Grue was a dozen times harder.  Like another language.



Live knee vuh yife?  Knife?  The knife.  He needed it.



I let myself fall onto my front, face toward the ground, so I wouldn't choke.  The knife-holding hand stayed put, but my arm bent at a bad angle, eliciting a stab of pain.  My wrist and elbow awkwardly twisted, strained to return to a natural position.  I resisted the urge to let go, kept my grip on the knife handle.



The ground gave before I did, and the knife came free.  My arm straightened, stretching out in front of me, the knife gripped in my black gloved hand.  I looked up from the knife to see a blurry image of Grue struggling under his bonds, the last thing I saw before darkness and merciful lack of consciousness claimed me.





