





``Hey Taylor, wake up.''  A girl's voice.



``Taylor?''  A deeper, more adult voice, ``Come on, kiddo.  You've done really well.''



I felt warm, fuzzy.  Like waking up in a warm bed on a cold day, all the covers in the right place, feeling totally rested, knowing you don't have to get up right away.  Or like being six years old, having crawled into bed with Mom and Dad at some point during the night and waking up between them.



``I think she's gradually coming to.  Give her a moment,'' Someone older.  An old man, maybe.  Unfamiliar.



``I was worried she wouldn't wake up,'' the deeper male voice said.



``Could have told you she wasn't in a coma,'' the girl replied.



``The same way you're absolutely, one hundred percent positive she doesn't have a serious brain injury?'' the old man asked. ``Because narcotics can camouflage the symptoms, and if we wait too long to take action on that\ldots well.''



``Nothing beyond what I described to you,'' the girl said, just a bit testily, ``Unless your equipment is faulty.  I need \emph{correct} information to work with, or I get false info.''



``I assure you, my equipment may be limited, but it is in perfect working order.''



I tried opening my eyes, found everything too bright.  Foggy, like I was looking at it from underwater, but my eyes were sandpaper dry.  Something dark moved over my vision, made my eyelid flicker.  Something else tickled my cheek.  I tried to raise my hand to my face to brush at them, but my arms were at my sides, buried under sheets and I didn't have the strength to move them.



``Hey sleepy,'' the deeper voice once more.  I felt a large hand rest on my forehead, it moved to brush my hair back, reminded me of my mom and dad again.  Being a kid, being taken care of.



The old man and the girl were still arguing.  Her tone was impatient ``--a concussion, severe blood loss, bruising, external and internal, plus whatever it is that fucked with her nervous system, understand?  I have no reason to lie to you.''



``All I'm telling you is that if there \emph{is} something else, and complications result, it's on you, because I'm taking your word on this.  I would rather the girl not die or wind up brain damaged, of course, but if she does, I won't feel guilty, and I--''



``If something happens because I was wrong, and it isn't because you gave me the wrong information or tools to work with, I'll own up.  I'll tell him, and your reputation will be unaffected.  Promise.''



The old man grumbled and mumbled, but didn't say anything more.



I tried opening my eyes again.  I recognized the face.  Brian.  Lisa joined him at the bedside.



``Hey there,'' she said, her tone sympathetic, ``You got walloped, huh?''



``Guess so,'' I replied, except I wasn't sure I said the `so' out loud.  I might have been drifting back to sleep, but another tickle at my face made me wrinkle my nose.  ``What is-?''



``That, honey, is the only reason we've been trying to wake you up.  You've been using your power while you sleep, and every bug in the neighborhood has been gathering here to crawl on you.  Not all at once, not all together, but they're adding up and someone's going to notice.''



Brian looked across the room, '' We've got the windows and doors sealed with saran wrap and tape, and they're still getting in.  Can't take you anywhere like this, and the good doctor here needs us to clear out in case a real patient comes in.''



``What I need is a sterile work environment,'' the old man groused, ``One that isn't ridden with cockroaches and--''



``We're handling it,'' Lisa snapped at him.  Then, in a softer voice, she said, ``Taylor, don't go to sleep.''



I was surprised to realize I \emph{was} drifting off.  Funny.



``I know the painkillers are nice.  We gave you boatloads, since you were really hurting.  But we need you to send them away.  The bugs.''



Oh.  I dimly recalled telling my bugs to come to me not long before I passed out.  I guess I hadn't ever told them to stop.  I guess blacking out had prevented me.  I sent an instruction, then told her, ``Good as done.''  Something caught my attention. ``Hmm.  Interesting music.''



``Music?''  Lisa momentarily looked very concerned.  She looked at Brian.



``Outside.  In front of the door.  An iPod, maybe.  There's a guy, listening to music.  Maybe he doesn't have the headphones on or the buds in his ears.  Or they aren't plugged in to the iPod itself.  Sounds like orchestra, or pop.  It's Latin?  Or English?  Both?  That last bit sounded Japanese.  Or Chinese.  Is it racist I can't tell the difference?''



``You're babbling, Taylor,'' Brian said, not unkindly.



Lisa briefly disappeared from my field of vision, ``But she's right.  There's a guy on the steps out front, listening to music.  How did you know?''



``Moth on the door.  I was so busy listening, I forgot to make her go.  I'm sorry.  I'll\ldots I'll--''



``Shh.  Relax.  It's fine.  Just send the bugs away, and you can go back to sleep.  We're handling everything, okay?''



It \emph{was} okay.  I drifted off.



\sectionbreak



I was jostled from a dream.



``Careful!''



``I am being careful.  Stop being so twitchy.  Just close the car door.''



``I'm \emph{not} being twitchy.  You almost dropped her a few seconds ago.  I swear, if you drop her on her head\ldots''



``I won't,'' the words were a bass vibration against one side of my body as much as they were a noise in my ears.  I was warm on that side of my body, too.  It smelled nice.  Like leather and shaving cream.



I started to say something, then stopped.  Too much effort.



A girl's voice sounded not far from my ear.  ``Hey there, Taylor.  Making a bit of a sound?  You waking up?''



I shook my head and pressed my cheek harder against the warm body.



She laughed.



A knocking sound.  The classic rhythm of `shave and a hair cut, two bits.'  The door opened a moment later.



``God, Taylor.  Is she?''



The girl – Lisa, I recognized it now – responded, ``She's okay, just sleeping.  Like I said on the phone--''



``I'm sorry to interrupt, just\ldots I'm sorry, I've completely blanked on your name, but can I help you carry her inside?''



``Actually, I'm alright, and I think I'd be \emph{more} likely to drop her if we tried to adjust to a two person carry.  The name's Brian.''



``Brian, okay.  Thank you.  If you could just bring her through here.  After you called, I didn't know what to do with myself.  I made up the sofa bed, in case we couldn't get her upstairs, or if there was a wheelchair.  I was thinking the worst\ldots''



``The couch is fantastic,'' Lisa said, ``She's most definitely not in the worst shape she could be in, or even close to it.  She's going to sleep a lot, and you'll need to check on her every half hour to make sure she's okay, for the next twelve hours.  Besides, she might want to watch TV between naps, so this looks like a perfect place to be.''



``Okay.  Good.''



I was laid out flat, and instantly missed the warmth and closeness I'd had moments before.  Then someone pulled dryer-warmed covers and a heavy comforter around me and I decided I could cope.



``Would you come through to the kitchen?  Our house is small and I'm afraid there's nowhere to sit in our living room with the sofa bed out.  In the kitchen, we'll be quieter.''



``But still able to see if she wakes up,'' Lisa answered, ``Makes sense.''



``Can I get you anything?  Tea, coffee?''



``Coffee, please,'' Brian replied, ``Long night.''



``Would it be okay if I asked for tea, when you're already busy with coffee, Mr. Hebert?''



``After all you've done, making tea is the least I can do.  But please, call me Danny.''



If I'd been comfortable in a morphine induced haze before, I was very, very awake the moment I heard the name and realized these voices and names I recognized had no business being together.



Dad, Lisa and Brian.  At my kitchen table. I kept my eyes half-shut and hung on to every word.



``She's okay?''



``Like I said on the phone, she's alright,'' Lisa said, ``Concussion, bruising, some blood loss.  Nine stitches.''



``Should I take her to a doctor?''



``You \emph{can}.  But my dad's a doctor, and he looked her over in his clinic.  Pulled strings to get her a CT scan, MRI.  He wanted to be absolutely sure there was no brain damage before he gave her stronger painkillers.  Here.  I've got the bottle in one of these pockets.  There.  It's codeine.  She's probably going to have some major headaches, and she was moaning in her sleep about pain in her extremities.  Give her one pill four times a day, but only if she feels she needs it.  If she's okay as is, just wean her off.  Two a day, or half a pill four times a day.''



``How much?''



``The codeine?  Four pills--''



``The CT scan, MRI, prescription.  If you just give me a second to grab my wallet, I'll give--''



I could picture Lisa taking hold of his hand, stopping him.  ``She's a friend, Danny.  My papa would never even \emph{hear} of having you pay.''



So surreal.  Hearing words like my dad's name or the word `papa' from Lisa's mouth.



``I\ldots I have no words.  Thank you.''



``It's fine.  Really.  I feel guilty--''



``\emph{We} feel guilty,'' Brian cut in.



``--for letting it happen.  That Taylor got the brunt of it.  And I'm sorry that we didn't call you sooner.  We had to wait for Taylor to wake up and get coherent enough to give us your phone number.''



I was pretty sure I hadn't.  Which probably made this one of those creepy Tattletale moments where she had been able to figure out something I wouldn't have guessed she could.



``I – that's alright.  Your other friends are okay?''



``Rachel's more scratched and bruised than Taylor, but she didn't get a concussion, and she's a tough girl.  My guess is she's sleeping soundly at home, and she'll be up and about this afternoon.  Alec, our other friend, passed out when it happened, woke up with a bad headache, but he's alright.  We've been teasing him about how he fainted, and it's bugging the f-, uh, it's bugging him.  As if guys never faint.''



``And you two?''



``A little worse for wear, but you could tell just by looking at us, obviously.  Scrapes, bumps, bruises.  I got burned, just a bit.  No worse than a bad sunburn.''



``Not around your eyes, I see''



Lisa laughed, so naturally you'd never think twice about it, ``Yeah.  I was wearing sunglasses when it happened.  It's that noticeable?''



``Not so bad, and if it's like a sunburn, you'll be fine in a few days.  Can you tell me more about what happened?  On the phone, you said something about--''



``A bomb.  You've seen the news?''



``Explosions across the city all night and all morning, yes.  The incident at the PHQ.   All started by one of the parahumans.  I can't remember her name.  Sounded Japanese?''



``Bakuda, right?  Yeah, pretty sure that's it.  We were cutting through the Docks on our way back from the Lord Street Market, and I guess we were in the wrong place at the wrong time.  One second, everything's normal, then disaster.  Brian was carrying Taylor's bags while she retied her shoes, so she was a bit behind the rest of us when it happened.  Brian and I stood up after the explosion, and Alec, Rachel and Taylor didn't.  Taylor was the scariest to see lying there, because you could see the blood right away.''



``God.''



I opened my eyes to peek and saw my dad at the kitchen table, his face in his hands.  I swallowed a fist sized lump of guilt and shut my eyes again.



Brian's voice.  ``I feel bad about it.  I shouldn't have walked ahead of Taylor while she was tying her shoes, or--''



``Brian.  If you had been standing beside her, you would have wound up in the same shape as her and you wouldn't have been able to carry her,'' Lisa objected. ``It was my fault for suggesting we cut through the Docks.''



``I have to ask--'' My dad started, ``Why\ldots?''  He trailed off, unable to find a good way to phrase it.



``We normally wouldn't take a shortcut through that part of town,'' Lisa said, ``But there were five of us, and you know\ldots look at Brian.  Would you want to mess with a big guy like him?''



``Gee, thanks, Lise,'' Brian said.  Then he and my dad laughed together.



So surreal.



``I\ldots I know it sounds strange,'' my dad spoke, hesitantly, ``But even after you told me it was a bomb, on the phone, I couldn't believe it.  I thought maybe it was a mean prank, or Taylor had come across, um.''



``The bullies,'' Lisa finished my dad's sentence.



``You know?''



``She explained a lot of it, including what happened in January.  All of us made it clear we'd help if she asked, however much or little she wanted.''



``I see.  I'm glad that she found someone to talk to, about it.''



Sympathetically, Lisa answered, ``But you're disappointed that someone wasn't you.''



If guilt caused you physical pain, I think that would have been like a shiv through my heart.



My dad, inexplicably, laughed, ``Well, aren't you eerily on target?  Taylor did say you were smart.''



``She did, did she?  That's nice to hear.  What else did she say?''



My Dad laughed again. ``I'll quit now, before I say something that she would rather I keep private.  I think we both know she plays things close to the vest.''



``Too true.''



``There's homemade cookies in the jar, there.  Still warm.  After I got the couch ready, I didn't know what to do.  Had to work out the anxiety somehow, so I baked.  Make yourselves at home while I see to your tea and coffee.''



``Thank you, Danny,'' Lisa said, ``I'm going to go to the living room and check on Taylor, if that's cool?''



``Please do.''



``Just gonna grab a cookie first\ldots Mm.  Smells good.''



I shut my eyes and pretended to be sleeping.  I could hear Brian talking to my dad in the other room, something about my Dad's job.



``So?'' Lisa asked me in a quieter voice, as she climbed onto the sofa bed to lie beside me, ``Does the story pass muster?''



I thought about it, ``I don't like lying to my dad.''



``So we did the lying for you.  Unless you want to tell him the truth?''



``No, but I don't want you here.''  The mental brakes that should have stopped my lips from moving failed to keep the words from leaving my mouth.  I closed my eyes, feeling the heat of a flush on my cheeks.



``I- I'm so sorry\ldots That came out wrong.  I'm grateful for what you did, what you're doing.  You guys are awesome and hanging out with you has been some of the most fun I've had in years.  I'm so glad you're here, and I'd like nothing better to just kick back and unwind after all that, but--''



Lisa put a finger against my lips, silencing me.  ``I know.  You like to keep different parts of your life separate.  I'm sorry, but there wasn't a way around it.  You were hurt, and we couldn't keep you without your dad causing a stir.''



I lowered my eyes, ``Yeah.''



``You're probably going to be a little wobbly for a few days.  Your, um, brutal honesty just now was probably the concussion at work.  It's going to influence your mood, maybe loosen your inhibitions as if you were a bit drunk.  Your memory might be a little unreliable, you might be more disorganized, or you might have extreme mood swings, like crying jags.  You might have a harder time reading social cues.  You work on getting through all that, we'll shrug it off if you say something you normally wouldn't.  Just\ldots try not to let anything private slip around your dad, so nothing slips?  All of this should pass before too long.''



``Okay.''  That last part was something of a relief.



Brian joined us and sat on the corner of the bed opposite where Lisa was lying, by my feet.  ``Your dad's an alright guy,'' he told me.  ``Reminds me a lot of you.''



I didn't know what to say to that, so I just said, ``Thanks.''



``Even after you've recovered most of the way, I think we'll go out of our way to stay out of hairy situations, at least for a little while,'' Lisa said.  Brian nodded.



``I like that idea,'' I replied. ``So what really happened, last night?''



She moved her head so she was sharing my pillow, ``Starting from when?''



``From when Alec crashed the car.  One second everything's fine, the next, I can barely move, barely think.''



``She was playing possum.  I was busy looking after Alec, assuming you guys were watching her. At the same time, you and Brian, I guess, were assuming I'd keep an eye on her.  While we weren't paying attention, she loaded her grenade launcher and shot you.  It should have burned you, but I think your costume saved you, there.  Your costume couldn't do much to prevent the concussion, though.  There was some secondary effect, where it did something to your nervous system.  Like being jabbed with a Taser, but more about incapacitating you with unadulterated pain than knocking you out.''



I shivered.  Just remembering what it had felt like made me twitch, like I was hearing nails on a blackboard.



``I was farther away, and I think your body shielded Brian, or maybe his power helped, because we didn't get hit half as hard.  It was still enough to put the two of us down long enough for Bakuda to load and fire two rounds of that gluey string crap.  Once that happened, we were pretty fucked.  Until you turned the tables.''



``I stabbed her foot,'' I remembered.



``Cut off two and a half of the toes on her left foot.  One of which had a toe ring.  Brian said you pushed the knife towards him as you passed out.  He blacked out the area, managed to reach the knife, cut himself free, and then rescued the rest of us.''



``And Bakuda?''  I whispered.



``One of two bits of bad news.  She got away while Brian was getting free and helping us.''



``Fuck!'' I said, a touch too loud.



Brian sounded apologetic, ``You were in bad shape, I wasn't sure what had happened to Regent, and Lisa was a little feeble from the same blast that messed you up like it did.  I could maybe have caught up to Bakuda, stopped her, but I decided making sure you guys were okay was more important.''



I nodded.  I couldn't exactly argue with that.



Lisa continued, ``I called the boss, he sent us to a doctor who has a reputation for being discreet and working with parahumans.  Been doing it twenty years.  We were worried about you.''



``Sorry.''



``Nothing to apologize for.  Anyways, it all more or less worked out.  The doc got the capsule out of Brian's nose, patched you up, gave Regent an IV.  I sat and watched you while Brian went and got Rachel, her dog and the money.  Only two or three thousand gone, that someone thought they could get away with grabbing from the bag before it was all counted.  Our boss sent a van and picked it up a little after midnight.  Money he gave us is already in our apartment, with more to come after he decides what the papers are worth.''



``You said it \emph{more or less} worked out, and you still haven't told me the second piece of bad news.  What aren't you saying?''



She sighed, ``I was hoping you were too out of it to ask.  You really want to know?''



``Not really.  But if I'm going to lie here for a while, getting better, I don't want to be left to imagine worst case scenarios.''



``Okay.''  She fished inside her jacket pocket, then handed me a newspaper clipping.  Except it was torn, not clipped.  Newspaper ripping?  Across the top, in big bold letters, was the word `Escaped'.



When I tried to read the article, though, I found I couldn't keep my eyes fixed on one line.  ``Read it to me?''



``I'll give you the cliff notes.  Just before she started to come after us in the Jeep, Bakuda gave the order to put another plan into action.  Bombs started going off all over the city.  Blowing up transformers to deny power to entire districts, a school, a bridge, train tracks\ldots the list goes on.  People are freaking out.  Front page news, it's on every channel.  They're saying at least twenty people confirmed dead so far, with other bodies yet to be identified, and that's not counting the four people she blew up when she was holding us at gunpoint.''



A vivid image of what had happened to Park Jihoo flashed through my mind's eye.  He died.  He's really dead.  I never knew him, but he's gone forever, and I couldn't do anything to save him.



``Here's the second bit of bad news.  All of that?  It was one overblown distraction.  Something to keep every cape in the city busy, while Oni Lee sprung Lung from the PHQ.''



I let out a long sigh.  ``Oh fuck.''



``The city is a warzone right now.  The ABB is twelve times the size of what it was two weeks ago, and Bakuda's gone on a rampage.  More bombs are going off every few hours, but they're not aimed at major services this time.  Businesses, tenements, warehouses, boats.  My guess is she's targeting places the other major gangs and factions in the city hang out, or places they might hang out.  I don't know what's going to happen.''



``You'd think having a third of her toes cut off would slow her down, if anything,'' Brian said.



Lisa shook her head.  ``She's in a manic phase.  She'll burn out, if she hasn't already, and the explosions will stop in a matter of hours.  With Lung reinstated as leader, though, that doesn't mean the ABB is going to lose any steam.  Chances are he'll capitalize on the advantage Bakuda created for him.  It's just a question of where, when, and how much.  Depends on the shape he's in.''



We didn't get a chance to talk further on the subject.  Tattletale raised a finger to her lips, and we shut up.  A few seconds later, my dad walked into the living room, holding a tray.  He put it in my lap.  Three mugs, a plate of cookies and two toasted bagels, one with jam and one with butter.



``I've got another bagel in the toaster, so help yourselves and ask if you want more.  Green mug is Brian's coffee.  Tea for you girls.  Here you are, Lisa.  Woodstock mug is Taylor's favorite since she was a kid.  Here.''



Brian chuckled a little as I accepted the mug with two hands.



``Hey!  No laughing at me while I'm like this.''



``Which reminds me, how long before she's okay to return to be up and about?'' My dad asked Lisa.



``A week, bare minimum,'' Lisa replied, ``Maybe escort her to and from the bathroom until you're sure she's steady on her feet, but beyond that, probably best if she stays in bed, stays home and takes it easy until next Saturday.''



That stopped me.  ``What about school?''



Lisa nudged my upper arm with her elbow and grinned, ``You got a perfect excuse not to go.  Why complain?''



Because I'd forced myself to go to school after missing nearly a week of classes, with the intention of not skipping any more, and now I was going to miss another full week.  I couldn't say that, especially not in front of my dad.



``Okay if we stay a bit?'' Lisa murmured in my ear, the moment my dad left to get the third bagel.



``Yeah,'' I admitted.  The damage was done, so to speak, they were already here.  I might as well make the best of it.  I scooted over so Brian could sit on the bed, just to my left, and Lisa got up for just a second to grab the remote.  She found a movie that was only a few minutes in as she settled in on my right.



I momentarily dozed off and woke to realize my head was resting on Brian's arm.  Even after my eyes opened and I started focusing on the movie again, I left my head where it was.  He didn't seem to mind.  The three of us laughed at a series of jokes in the movie, and Lisa got the hiccups, which only made Brian and I laugh harder.



I saw my dad puttering about in the kitchen, probably to keep an eye on me, and our eyes met.  I gave a little wave, not moving my arm, just my hand, and smiled.  The smile he gave me in return was maybe the first truly genuine one I'd seen on his face in a long time.



The school thing?  I'd worry about it later, if it meant I could live in the present like this.





