





Kayden crouched by the crib, her arms folded over the edge, watching her baby's chest rise and fall.  She felt at peace.  Aster was perfect, flawless, untainted by the chaos and the evils of the world beyond the apartment and the nursery.  Even in her waking moments, she wasn't overly demanding, quick to reduce her wails to quiet whimpers when she heard assurances that food, company or a diaper change were on the way.  Not that she understood, of course, but she trusted her mother would provide.  Kayden couldn't have asked for more.  Literally, there was nothing Aster could do, have or be that would make her better than she was.



In an odd way, Kayden supposed, she took refuge in Aster.  She found succor in the company of her child, in the midst of a world she had little hope for.



It took willpower to force herself to step away, to quietly step from the nursery and half-close the door behind her.  When she saw pudgy fifteen year old Theo sitting in front of the television, she was momentarily disoriented. Then she felt a stab of guilt.  She'd forgotten about the boy, in the midst of caring for Aster and her preparations for the night.



``Theo, I'm sorry,'' she spoke.  The boy had been captivated by the final votes of some reality TV show, but he didn't give a second thought to muting the TV and giving Kayden his full attention.  ``I've been so preoccupied, I haven't fed you.''



``It's okay,'' Theo answered her, breaking eye contact.  It wasn't.



``Look, I'm going out-''



``In costume?''



``Yeah,'' Kayden replied.  She tried to read the expression on the boy's face, but Theo was a stone wall.  He'd had to be, really, with what he'd grown up with.



Resisting the urge to comment or push the boy to offer some commentary, criticism or support, Kayden continued, ``I'm leaving you thirty dollars here on the kitchen table.  If you want to use it to order out, please feel free.  Otherwise, raid my cupboards, my fridge, or use the money to go down to the convenience store in the lobby, okay?  If you decide to rent a movie, leave it here for me to take back.  I might want to watch it.''  Kayden smiled, trying to coax a matching expression from him.



``Okay,''  Theo said, his face blank.  ``When will you be back?''



\emph{In time to take you back to your dad's}, Kayden almost said.  Then she had an idea, ``I might be late.  Would it maybe be okay if you spent the night?  You'd just have to check in on Aster every few hours.  Keep an ear out in case she cries?  I'd pay you for the full night's babysitting.''



The times when Theo let a glimmer of emotion show were few and far between.  A smile, genuine, touched Theo's face, and almost broke Kayden's heart in the process.



``I'd love to,'' Theo replied, meaning it.



``Then it's settled.  Sorry to interrupt your show,'' she said.



``It's fine,'' Theo said, just a touch too fast.  It wasn't fine, apparently, but he would never admit it.  \emph{Could} never admit it.  Kayden felt a flicker of hatred for the man who had eroded every ounce of personality and assertiveness from his son.  She would give her right hand for a smart-alec remark, rolled eyes or to be ignored in favor of a TV show.



She had to console herself that she was at least giving Theo a night's respite from the man.  It wasn't enough, of course, but there was so little she could do.  All she could offer were small kindnesses, little gestures of love and affection, and hope they helped.  With that in mind, Kayden took the time to get some sheets out and set up the other couch so Theo would be comfortable when he was done watching TV.



When that was done, she double checked the TV to see that she wasn't interrupting anything, and told Theo, ``Wish me luck.''



``Good luck,'' the boy replied, in a tone that was all affectation.  The false words stung Kayden more than if Theo hadn't said anything at all.  Tonight wasn't the night to confront that issue.  She left the apartment, locking the door behind her.  She took the stairs up to the roof, and shucked off her bathrobe.   The garment went in the gap between two flowerboxes, where nobody would find it unless they were looking for it.



Then she stepped off the edge of the roof.



The wind ripped at her hair, blew cold against her face.  As she tumbled head over heels, seeing only glimpses of the streetlights and cars below her, she waited.  Her apartment building was fifteen stories tall, which gave her less time than one might expect.  All it would take was one second of doubt, one mistake, a momentary hesitation, and she would hit the ground.



\emph{Aster}.  It was fitting that she thought of her daughter.  She always did, these days, every time she jumped.  It had become a ritual, as though she couldn't set out to clean up the city if she didn't remind herself \emph{why} she was doing it.



Energy suffused her body.  The entire sky lit up in a brilliant, blinding flash of light.  By the time the spots cleared from the eyes of the people on the street, she was already gone, hurtling over Downtown Brockton Bay, a white trail of light following behind her.



Kayden didn't wear a mask, but it wasn't necessary.  With her powers active, her brown hair and eyes became a radiant white, emanating a light so brilliant it was impossible to look straight at her.  The fabric of her alabaster costume, too, radiated with a soft glow that rippled like light on the surface of the water.



Her usual routine was to patrol for an hour or two, get a sense of things, and then take action where she thought it was most appropriate.  Tonight, though, she was frustrated, and she hadn't even begun.



A year ago, she had made the ABB a priority target.  Three to five times a week, she had carried out surgical strikes against the low level operations of the gang, interrupting shipments, beating up dealers and thugs, attacking their places of business and all the while, she had been gathering information.  That information had paid off from time to time; she had clashed directly with Lung on no less than four occasions, had encountered Oni Lee on two.  In all but one of those encounters, she had successfully forced them to retreat, to abandon whatever it was they were doing at the time.  Those were the good days.



There had been bad days too.  Most of the time, she made a point to rough up the lower level members of the gang when she'd taken them down, enough to make them reconsider their career choice.  Make them consider going to another town.  At one point, Lung had set a trap for her, and succeeded in returning the favor.  It had taken her two months to recuperate from all of her injuries.  Other days, which were somehow worse, she found herself struggling to make a difference, coming to the dawning realization that she had failed to change things.



This week had been a long series of those bad days.  When she'd read in the news that Lung had been apprehended, she'd cleared her schedule.  Kayden had taken her vacation days and called Theo about babysitting.  It had been the best chance she'd get, she thought, to clean up the ABB once and for all.  Get that scum out of her city, while they were leaderless.



Five of her seven vacation days had passed, and she'd accomplished nothing.  Less than nothing.  They were getting stronger.



Breaking her usual patrol route, she headed straight to the northern part of the city and investigated the Docks.  It was empty of ABB members, aside from two Korean girls were taking a break from turning tricks near the ferry, talking to their aged, fat, matronly pimp.   Kayden resisted the urge to take action and run them off, resisted grilling them for information.  She had done that last night with a group of dealers, and accomplished little to nothing.



The ABB was still active.  Even with their boss gone, they were more organized than they had been under Lung's influence.  But her interrogations had failed to get any details on why.  Even broken arms and legs hadn't hurt or scared the thugs enough to get them talking about what was going on.



This was the situation, usually, where Kayden would go to informants for information, resurrect old alliances and get help in squashing the ABB before they could get their footing again.  She had hunted down old buddies, contacts and teammates three days ago, and had been frustrated by the lack of response, the lack of enthusiasm.  Max, Theo's father, was to blame for that.  Just as she'd left his team a more broken person than she'd been when she joined, others had gone through the same experience. With charisma and a keen sense of people, Max had convinced people from across the country to join his team.  Just as easily, he'd tore them apart without them realizing he was doing it.  Confidence broken, wracked by doubts, paranoid regarding everyone except the one man that had caused the paranoia in the first place, they'd splintered off from the team.  Not that Max minded.  There was always a fresh supply of bright eyed recruits ready to replace anyone he broke.



Now most of the gang was gone, quite possibly on a big job, and she had no idea where.  She had no idea where to find out.  Kayden grit her teeth.  This wasn't working.  If she was going to make any headway before her vacation days were up, she had to act now.  Make a deal with the devil.



She returned Downtown.  It was hard to navigate the streets from so high up, even if they were roads she traveled on a daily basis as her uncostumed self.  From here, the buildings all looked the same, with mirrored outsides and gravel rooftops.  Twice, she circled around the top floors of the wrong buildings, looking for the logo set on the side of the building would mark Max's building apart from the others.



The black crown against a red and yellow background.  She stopped when she saw it, cursed under her breath.  When she approached, she saw him, still in his office.  Not so unusual, he'd worked late during every night of their marriage.  He had a laptop directly in front of him, a sandwich in a paper wrapping to his right, and an array of papers spread over the desk to his left.  He swiveled around to face her as she got close to the window, smiled softly.



Damn him, he was five years older than her, pushing thirty five, and he was still the best looking man she'd ever looked in the eye.  Even the wrinkles at the corners of his eyes only made him more attractive.  He'd taken off his tie and suit jacket, and the sleeves of his shirt were rolled halfway up his forearms, forcing her to note he was still working out.



He waited, his hands clasped over his stomach, the faintest expression of amusement on his face.  She knew he was capable of opening the window to his office.  He was waiting for her to \emph{ask} to come inside.  It was the sort of little power game he was so fond of.



On another night, she would have tested her will against his.  To no avail, usually, but she would have tried.  It probably would have ended with her flying away, making it clear she could do without his assistance.  Tonight, though, she felt the frustration of her fruitless `vacation' and brought herself to reach out and knock on the window.



Before she could rap her knuckles against it a second time, it clicked and opened upward. She navigated her way around it to make her way inside. He hadn't seemed to move a muscle when he opened the window.  He liked little demonstrations like that.  She set foot on the carpet of the office and let the light glowing from within her fade.  Her hair stopped stirring and writhing in response to the energy rippling through it, going limp and turning brown.  Her eyes dimmed to their dark hazel color.  She could hear a click followed by the faintest of hisses as the window slowly closed behind her.



``Kayden.  It's been a little while,'' he managed to greet her and make it sound like a criticism in the same breath.  He half-turned to type on his computer, and the lights in the office adjusted to a halogen glare.  She shut her eyes briefly and basked in the glow, feeling her internal supply of energy recharge.



``Max.  Thank you for the light.''



``You're fine, I take it?''



``I'm fine.''



``And our daughter?''



``Aster's well,'' she said, as calmly as possible, as her heartbeat pounded in her ears.  She knew he didn't really care.  He was letting her know that he hadn't forgotten about Aster, reminding her that he, at any time, any moment, could take custody of her baby girl.  He had the money, he had the contacts.  She'd be helpless to stop him.  She remembered to mention, ``Theo's babysitting her tonight.''



``I know.  He called a little earlier to ask if he could spend the night.  I told him that was fine.  It'll do him good to spend time with you and Aster.  Some female influences in his life.''



Kayden answered with a curt nod.  To anyone else, this conversation would have sounded perfectly innocent.  As someone who had worked alongside Max for ten years and been married to him for one, she knew this was all negotiation.  He was making it clear he was doing her a favor, and he'd expect recompense at some point, tonight or a week from now.  It was how he was – always playing for power, for advantage, for dominance.  All the while, he was doing it in a way that you couldn't confront.  If she called him on it, he'd play innocent and she'd look like the crazy one, the one in the wrong.  Sometimes even to herself.



``So, what can I do for you?'' he leaned back in his seat.



``The ABB is lacking leadership.  Or, at least, lacking experienced leadership.  I want to take them down before they regroup.  To do that, I'm wanting to reunite our old team.''



``And you're admitting you can't do it without my help.''



``Yes,'' it pained her to admit.



``Not interested,'' he said, spinning around in his chair to face the computer.  There was a click, and the window behind Kayden began to open again.  As the air blew in from outside, a strand of hair blew across her face.  She tucked it behind her ear.



``I've talked to the others, but nobody that's worked for you is willing to be the first to join me.  Some say they're worried they'll offend you.  Others are just spooked, or they've already given up.  They ask me why would a group of your rejects do any better than they'd managed as part of your team?  I'm not getting anywhere, and time's running out.  All it would take would be one word from you, and I'd have a team of four or five people.  With that, I could root out and squash the ABB.''



Max stood up and sat on the edge of his desk so he was facing Kayden, ``I don't see it being worth the effort.  What's in it for me?''



``The ABB would be gone, for starters.''



``They'll be gone eventually.  I'm patient.  What else?''



``I don't have anything else to offer you, Max,'' she answered.  That was a lie, she knew\ldots but the closest thing she had to a bargaining chip was something she would never give up in a million years.  Never Aster.



``I want \emph{you}.  On my team again.''



``No.''



``You'd be my second in command.  I'd talk to the old members of the team, and get them to form a separate group to work under you.  You'd double check with me on anything you did, but other than that, you'd be completely autonomous.  Free to use your team as you see fit.''



\emph{Other than that}, she thought.  As if it was inconsequential, to be checking in with him on every move she made.  ``I don't agree with the way you do things.  I don't want to be associated with you.''



He laughed, throaty, deep, rich, while she stood there in stony silence.



``Kayden,'' he said, when he'd stopped, ``You're already associated with me.  People say our names in the same breath, even when we haven't worked together in two years.  When my name appears in the newspapers, yours is never far behind.''



``I'm working to change that.''



``And you'll be working against that impression for decades, to no effect, I guarantee you.''



Kayden turned and looked out the window, unwilling to look Max in his brilliantly blue eyes for any longer.



He continued, and she knew he was smiling smugly at her even without looking at him, ``Regardless of our different methods, we always shared the same goals.  To clean up this filthy world of ours.''



``You do it by putting drugs on the street, stealing, extorting.  I can't agree with that.  I never did.  It doesn't make any sense, to improve things by making them worse.''



Max smiled, ``It's ugly on the surface, but it's more money, more power, and it gives me the leverage to really affect things.  The only people I hurt are the same people who cause the problems in the first place.''



It was a refrain she had heard often enough before.  She folded her arms.



He changed tactics, ``Let me ask you – would you rather be doing things your way, failing to change things or would you rather work under me and make a difference?''



``I \emph{am} making a difference,'' Kayden answered, ``I'm working to make this world a better place.''



``Of course,'' he replied, and she didn't miss the hint of condescension in his voice, ``You left my team to go do good work, it's just pure coincidence that it's black, brown, or yellow criminals you target.''



Kayden frowned, ``Hard to avoid, when the only notable gang of whites is \emph{yours}.  Some old friends and allies of mine still work for you\ldots I can't go around attacking them, can I?  I'm working to improve our city, but I'm not going to beat up people I've been out to drinks with.''



``And in the process, you're doing little to shake the notion that you're a part of Empire Eighty-Eight,'' Max smiled, ``It's amusing to hear you try and justify your perspective, but you're ignoring the elephant in the room.  Cut the B.S. and tell me you don't feel something different when you look at a black face, compared to when you look at a white one.''



Kayden didn't have an answer to that.  It was his fault, really.  The high school baseball player she'd had a crush on when she'd been in middle school had wound up being the same person that first approached her when she started going out in costume.  Blinded by his good looks and his way with words, she'd been swayed, convinced of his way of thinking.  She'd tried to change her outlook since the divorce, but she had seen a great deal in her ten years as a member of his team.  It was impossible to look at the city now and ignore the fact that too much of what made it an uglier place to live and raise a child in could be traced back to the same kinds of people.  Sure, the whites had criminals too, but at least they were fucking civilized about it.



When no response was forthcoming, Max said, ``That's what I thought.  However our methods differ, regardless of whether you're willing to admit it out loud, I think we share a very similar perspective.  My offer is this:  Let me prove my methods work.  Join my team, serve as my second in command for one more year.  Only person you answer to is me, and I give you a team of your own.  You can handpick your own squad from our prospective members and ex-members, though I can't guarantee every person you name will come running\ldots''



``Max\ldots'' Kayden shook her head.



``The final part of the deal is this.  If you aren't satisfied with how things went when your year is up, Empire Eighty-Eight is yours.  Lock, stock and barrel, including my business, every employee, every asset, legitimate or otherwise.  \emph{I} become \emph{your} second in command, and I follow \emph{your} orders.  You can make Empire Eighty-Eight into a humanitarian effort, sell the business, turn us all into superheroes.  I don't care.  If I can't impress you, then what I'm doing simply isn't worth holding on to.''



That caught her attention.  Years ago, Kayden probably would have snapped up an offer like this without a second thought.  Being married to Max for eleven months, waking up to who he really was, it had given her perspective and caution.  She considered for a few long moments, trying to figure out the angle.  He was telling the truth, she knew.  Whatever else Max was, he wouldn't break his word on something like this.



``Is the business failing?''  She asked.  Was she getting a booby prize?



``Thriving.  Promise.''



``What would you have me doing?''



``The same thing you did before.  You'd be my heavy hitter.  My enforcer.  If I needed you to make an example of someone, you'd do it.  Only difference between then and now is that my Empire is bigger.  Better.  You and I can make a greater impact.''



\emph{More blood on my hands}.  As the thought crossed her mind, she looked at her gloved hands.  Pristine white cloth, stark in glare of the halogen lights.  She knew what he was doing, had known when she decided to come.  He found a person's weakness, attacked it, turned it to his advantage.  He'd known she was frustrated with her efforts as a solo agent, had probably had this conversation planned out days or weeks ago, playing it out in his head, having an answer ready for anything she could say.  How could she compete with that, when she rarely looked beyond the next twenty-four hours?  It was just how she was, how she thought.



Which was probably why they were so effective as a pair, she was forced to admit.



``So I ask you again, Kayden, do you want to spend your time failing to make a name for yourself on your own, or are you willing to join me in actually changing things?  Come with me, and I guarantee you win one way or another.''



Her eyes lit up, and her hair began to turn white from the roots outward.  In moments, she was her radiant alter ego\emph{.  }Purity.



As if in response, he picked up a letter opener and held it in front of his chest.  Blades of metal began to branch out from it, each forking out into more.  Slow at first, the network of metal swiftly encompassed his chest, then the rest of his body.  Bars, blades, tubes, sheets of the metal found their place around him.  With his power, she knew, he could bring metal to sprout from any solid surface around him, including the metal he had already created.  As readily as he could bring thirty-foot spears of iron to erupt from the ground or walls, he created a finely worked suit of armor, then embellished it with blades and curling spikes.  He finished it with an uneven crown of blades.



He extended a gauntlet, left it there for her to take.  It was the smallest gesture, he \emph{never} made a move where someone could refuse him, leave him hanging, and it meant the world to her, even as she suspected it was calculated for just that effect.



\emph{Forgive me, Aster,} she thought.  \emph{I'm doing this for you.}





