





A whistle.  Brutus' ears perk up.   Already jumping off the bed as second whistle comes, just after the first.  Two whistles like that means come.  Master only asks for dogs to come to the front stairs if it is time for walkies!



Walkies are Brutus' favorite thing!



Other dogs are bumping shoulders with Brutus in hurry to get to Master.  Turn corner too fast, claws scratch at floor to get grip.  Fall a little.  Judas hesitates, sniffs, but Angelica is ahead of Brutus now.  Bad girl.  Brutus snarls a little at Angelica, she backs away, drops behind.  Brutus is top dog.  Angelica should know that.  Brutus arrives at Master first, the way it should be.



Brutus is top dog, but Master is alpha.  Leader of this pack.  Not leader of her people-pack but that is okay.  She bends down and scratches all over Brutus' neck and shoulders, deep, rough.  Perfect scratches because they dig through Brutus' thick fur.  Tail is wagging so hard that back paws are slipping on floor.  Fall over and turn belly up so Master can scratch it.  She does and it is ecstasy.



Master is hurt and hurting.  Brutus knows this.  When she bends down, she is moving more slowly, she is making little sounds as she makes bigger movements like bending down and standing up.  She smells like dried blood and stress and sweat in ways she usually doesn't.



``Angelica, Judas, stay,'' Master says, ``Not taking you two.'' Brutus doesn't understand but Master sounds apologetic.  Like when she was walking up stairs and accidentally kicked Brutus in chin because he was following too close behind her.  She scratches each of them in turn.  Not enthusiastic scratches.  They are happy to be scratched but they aren't coming for walkies.  Brutus' tail stops wagging.  Is Brutus not coming for walkies?



Master picks up leash.  ``Brutus, good boy.  Walkies?''  Tail is wagging crazy hard again.  Master tells Brutus to sit, Brutus sits.  Is good boy.  Master puts plastic bags in back pocket, puts on backpack.  Backpack unusual.  Master doesn't usually bring backpack for walkies.  Errand?



``We're going on an errand, okay boy?'' Master speaks.  Brutus' tail wags.  Brutus was right!  Errands always interesting.  Brutus eagerly takes a few steps forward before remembering to be a good boy.  Master doesn't like it when Brutus pulls on leash.  She puts on shoes, gets the keys that jangle, gets crinkly wrapper things she sometimes eats that Brutus can't because Brutus is a dog.  Crinkly wrapper things go in left pocket.  She gets treats for dogs to put in right pocket, stops.  Gives treats to Judas and Angelica.  Treat for Brutus?



``Treats later,'' Master says.  `Later' is familiar word but meaning unclear.  Brutus feels crushing disappointment as treats go in Master's right pocket.  Jumps up a little to remind Master she forgot to give a treat.  Master makes angry clucking noise and Brutus is sorry now.  Tail down, ears down.



``Bitch, hold up,'' speaks the scentless man.  Scentless man makes Brutus nervous because he is big but he has no smell.  But he is Master's alpha so Master stops and listens.



``You're going out?'' the scentless man asks.



``Work,'' Master says.



The scentless man waits for something, then speaks again, ``Are you okay?''



``Fuckin' peachy.''  Brutus knows Master only says fuck word like that when she's mad.



``I have a hard time believing that, to be honest.  You were in pretty rough shape when I found you with \"{U}ber and Leet's henchmen, and those guys from the ABB.''



``I'm fine \emph{now},'' Master tells him.  She sounds angry.  Brutus steps forward, ready to growl to add own voice to hers, but Master tugs on leash just a little and Brutus stays quiet.



``When I found you, one of them had you tied to the ceiling by your wrists and was using you as a punching bag.''



Master breaks eye contact.  Brutus knows this is a sign that Master sees the scentless man as her alpha.  When she speaks, she still sounds angry, ``I fucked up.  I was bored, restless, figured I'd walk Angelica and see if I could meet you guys where the money was.  Someone recognized me and tailed me.  I was stupid, I took my licks for it.  I'm fine now, we have the money, all is well.''



The scentless man sighs.  Sounds a little angry as he says, ``It's not\ldots no, nevermind.  No use getting into it.  But what if someone recognizes you while you're walking \emph{him}?''



``I'll fight back sooner, harder.  Or are you going to tell me I can't walk my dogs anymore?''  All of a sudden, Master is tense.  Brutus can see it in her legs, hear it in her voice, feel it in her grip on the leash.



``I wouldn't do that,'' the scentless man replies, his voice quiet, slightly strained ``And you wouldn't listen even if I did.  Just\ldots be careful.''



``I can go?''



``Go.  Enjoy your walk, both of you.''



And the tension leaves Master.  One small whistle and Brutus knows to follow.  Down the stairs and out the door into the outside world.  So many smells!  So many sounds!  So exciting!



But can't get too excited.  Brutus is good boy.  Doesn't pull on leash like Angelica still does.  Master always makes angry clucking noise at Angelica on walkies.



Master is walking slower.  Favoring one leg.  Brutus is eager for walkies but doesn't pull on leash even if Master is walking slower.



So many smells!  Being in own territory is good but being on walkies is smelling whole world.  Always new things, always new things to smell about old things.  Smell this pee and know almost everything about the dog who peed.  Bitch.  Maybe in heat soon.  Lives with kids.  Pee smells like stress and eating too much grass and sleeping too much and being a fat dog.



Smell that poo to know about dog who pooed.  Hungry dog.  Hungry dog's master probably hungry too.  Many like that here.  Not like that in Brutus' old home.  No people or dogs there were hungry.  But Brutus remembers being unhappy.  Master was always ignoring Brutus.  Leave Brutus in basement alone all day until Brutus stop bad man who came in basement window.  Is okay now.  Brutus is happy now with new master.



Smell that pee.  Human pee.  Not as interesting.  Master whistles to remind Brutus to keep up.  No more sniffing for now.



``Brutus, sit, stay,'' Master orders.  Brutus sits and stays while Master stands beside him.  Is good boy.  Gets scratched by Master.  Little female human is walking up to Brutus. Smaller than Brutus.  Pats at Brutus, pokes.  One poke in eye.  Brutus' ears down, head down, tail between legs.  Not good scratches.  Little human laughs.  Poke again in Brutus' side.



Brutus looks up at Master.  Pleading.  Master not saying anything so Brutus stays while being poked.  Little human grabbing Brutus' fur on side and pulling too hard.  Like Angelica when Angelica was new to Master's pack, biting and pulling and making Brutus bleed.  Bad memory.  Growl starts in Brutus' throat.



``No, Brutus, off,'' Master orders.  Brutus lowers head.  No more growling.  Still being poked.  Still being pulled at.



Big female human that smells like the little human arrives.  Is walking fast.  Big female stops and laughs at Brutus and little human.



``Aren't they cute?''  Another laugh.



Master doesn't laugh.



``Well, kids will be kids.''



Master speaks, her voice even but her body language is angry, ``Watch your fucking child.''  Brutus knows watch is order for Brutus to sit and stay and bark if anyone comes\ldots but Master is talking to big female and not giving order to Brutus.  Other word Brutus knows is fucking which means Master is mad but Brutus isn't the one she's saying fucking to so it is okay.



Brutus thinks maybe it's okay to growl now because Master said fucking so he growls.  Smells fear from little human and big female.  Master doesn't say no so it was okay for Brutus to growl.



Big female laughs but laugh sounds different than before, shrill.  Waves her hand.  Bends down to pick up little human.



``Brutus, guard,'' Master orders.  Brutus quickly looks at Master and Master is pointing at little human so Brutus moves between little human and big female and growls at big female.  Big female backs away.  Brutus smells lots of fear now.  Smells sweat and stress and hears little noises of worry and fear from both the big female and little human.



Big female steps to one side and Brutus moves to stay between her and little human.  She bends down again and Brutus growls, snaps at her fingers.  Is good boy.



Big female talks to Master, ``Please.  She was just doing what kids do.  She thinks all dogs are cuddly.''  Her voice is submissive, sounding like more worry and fear.



``Brutus, mouth.''  Brutus looks where Master is pointing and Master is pointing at little human.  Brutus obeys by grabbing little human's arm and holding it in his mouth.  Is good boy.  Little human howls and tries to pull away but Brutus closes mouth a little each time and little human soon understands that arm is staying in Brutus' mouth.



Then Master tells big female, ``He's an abused dog, you know.  Before I owned him, he was mistreated.  Until he hurt someone so badly they needed amputation.  I rescued him before he was put down.  And you just let your kid walk up to him and start clawing at him.  Do you understand what could have happened?  That he could have killed or maimed your fucking mouthbreather of a child?''



Brutus only knows his own name and word kill.  Other words don't mean anything to Brutus.  Kill is order to attack and not stop until that thing isn't moving anymore.  Master only gives Brutus and Judas and Angelica order to kill with squirrels and racoons and once a horse.  Big female is on knees now and fear smell is all Brutus can smell right now.  Is good to be lower than Master and showing submission.  Big woman is saying things but Brutus can't understand because she is talking and not stopping.



``Brutus, off.  Come,'' Master says and Brutus lets go of arm and walks to Master's side.  Little human still howling.



Then Master tells big female same thing as before: ``Watch your fucking child.''  Walkies begin again.  Get scratched.  Master says Brutus is good boy and Brutus is happy.  Tail wagging.



Is long walkies before Brutus and Master stop at a place that smells like blood and dog fear and dog rage and pee and poop.  Master knocks on door.  Man who opens door smells like blood.



Master and man talk for a while, and Brutus waits because Brutus is good boy.  Not paying attention to what they're saying because of smells.  Bad smells.  Sounds of dogs yelping and barking from inside the door.  Then Master says ``Stay'' and man starts touching Brutus.  Touches like vet touches, not like Master scratching.  Feeling each part of Brutus, fingers deep in fur to massage, check.  Hands on Brutus' private parts.  Says things that sound negative, shakes head.  Master talks some more.  Man stands and shakes her hand.



Master takes Brutus into the place that smells like blood and dog fear and dog rage.  Noisy.  Lots of people sitting in dark.  Smell like excitement and sweat.  Most lights are in middle of room where blood smell is strongest.



Man from door tells master, ``Put him right in the gate.''  Master puts Brutus in something like kennel that smells like rage and fear.



Man talks in loud voice and all the people in room howl and make more noise.  Man says Brutus' name.  He says kill which is a word Brutus knows.  But blood smell is so strong here Brutus can't pay attention to much else.  So much blood from so many dogs.  So many smells.



Then the kennel is open and Brutus has nowhere to go but center of room.  Can't go to Master because boxes are in way and there's another dog here bigger than Brutus that smells like rage and his own blood and other dog blood and death.



Then Brutus feels it.  Master is making Brutus stronger and it hurts but it's a good hurt.  Good hurt like when Brutus is stiff and stretches and joints snap and pop and Brutus feels better because of it.  Only this stretch doesn't stop and Brutus keeps popping and cracking and Brutus keeps feeling better and Brutus gets bigger.  Master usually takes longer to make Brutus this strong but Brutus is in room alone with the dog that smells like blood and death and Master must know Brutus needs to be stronger.



Soon Brutus is bigger than Master and as big as car and Brutus is strong.  Bad dog that smells like blood and death is cowering.



Then Master whistles twice which is order to come and Brutus is confused because there is no way to come.  Master whistles again and calls Brutus' name and Brutus lunges for boxes that are in the way.  Boxes break and Brutus can come to Master like a good boy.



``Brutus, guard!'' Master says and Brutus goes where Master is pointing, and that is door where all the people who smell like fear are going.  To get to door and guard it Brutus uses paws to push people out of the way and grabs one person's arm and flings her to one side like Brutus likes to fling favorite toys and person makes shrill howl.



Then Brutus is guarding door and people are running other way.  Reminds Brutus of squirrels and how squirrels run.  But people are not as fast or clever as squirrels and they don't play unfair by running up trees.



``Brutus!  Attack!'' Master shouts and Brutus obeys like a good boy.  Brutus uses paws and teeth and size to jump into the crowd of people who are running like squirrels and make them stop running.  Brutus knows it's bad to shake people like Brutus shakes toys or shakes squirrels.  No shaking.  No chewing.  Bite arm and leg only.  No biting heads.  Using paws is okay but claws aren't which is hard so Brutus mostly bites and slams into people with head and body to knock them over and make them stop.  Sometimes uses tail which is new and fun.  Brutus doesn't have tail when small.



Lots of people.  Every time Brutus thinks all people have stopped moving someone runs again.  Takes a long time.  Brutus' tongue lolls out, panting.  Tail wags and boxes break and Master makes clucking noise like Brutus did something bad.  No more wagging tail.



People lying on floor whimpering.  Smell like blood and fear.  Nobody running like squirrel anymore.



Master shouts, ``No more!''  and it is word for the people and not for Brutus.  Both are words Brutus knows.  No means bad and is for things Brutus shouldn't do.  More is what Master says when giving treats or throwing balls or filling bowls with food.  Brutus doesn't understand because one word is bad and the other is good.  But Master is alpha and Master knows so it is okay.



Master takes jangly keys from whimpering person and picks up cage with angry dog inside that smells like blood.  Master takes cage outside and puts it in car and tells Brutus to guard the cars.  Some people leave place but Brutus doesn't let anyone near cars.  Is good boy.  Master goes inside and gets more cages with angry dogs and puts them all in the car.  Then Master does it again.  Master gets backpack and uses ropes from backpack to tie cages together and tie cages to car.



Then Master goes inside for long time and doesn't come out.  People are gone so Brutus doesn't need to guard anymore.  Brutus goes to Master inside.



Master is kneeling beside cages and dogs inside smell like blood and poo.  But dogs aren't angry, aren't moving.  Brutus nuzzles master with nose and lies down beside Master and Master wraps her arms around Brutus' neck.  Master hugs Brutus tight for very long time.  Brutus knows it is a long time because Brutus stops being big and becomes smaller than Master.



Cars that make howling sounds start to come from far away and Brutus makes little barks like Master taught him.  Master gets up and takes Brutus into the car and gets in other door and the car starts moving.



Master opens and eats crinkly thing from pocket.  Master gives Brutus treat then rolls down window so Brutus can stick his head out in the wind and Brutus' tail wags because Brutus knows he was a good boy.





