





``I'll be there.  Yes--'' I saw a light in the living room window and put my hand over the lower half of my cell phone while I briefly investigated.  Damn, my dad was home.  I put the phone to my ear, ``I'm sorry, I've got to run.  No.  No.  Look--''



As I heard the front door open, I snapped the phone shut and jammed it into my pocket.  I'd apologize for hanging up later.  I definitely didn't want my dad to see the phone.  I didn't think he would stop me from owning one, but ever since my mom's death, cell phones had carried strong negative connotations.  That, and I'd have to explain where I got it and how I'd paid for it.



Brian had given me three identical cell phones – all disposables – first thing in the morning, and I'd decided to go with him to the loft rather than head to school.  The way I figured it, I didn't have much of a chance of focusing on classes with Thursday's bank robbery occupying my attention on top of the stress of just being there and waiting for the other shoe to drop as far as my skipped classes.  Besides, I rationalized, it didn't make a lot of sense to go if I knew I would be skipping again to go rob the bank.  I'd promised myself I would go the day after tomorrow.  Face the music.



I'd spent the day with the group.  Rachel had been out of the apartment, the others weren't specific on why and I wasn't interested enough to risk looking too curious by asking.  So it had just been me, Brian, Alec and Lisa.  We'd hammered out the fine details of the robbery and I had decided what weapons I wanted Lisa to ask the boss for.  I had elected for both a combat knife and a telescoping police baton.  The knife would serve for emergencies and those people who were just too tough to hurt with the baton.  The baton, twenty one inches long when fully extended, was for more general use, offering more clout than I'd otherwise get with my fists.  Lisa had promised I would have them for tomorrow.



After that, we kind of avoided the subject of the robbery, by some unspoken agreement.  It wouldn't do to overthink it or risk getting too nervous.  Either way, I had felt a need to burn some nervous energy, so I had helped clear out the storage closet around lunchtime, with Lisa and Brian's help.  We'd sorted out the stuff, found a place for it all, and set up the room with odds and ends they had lying around.  The stuff included an extendable clothes rack, a dresser, an inflatable mattress and a bedside table with a lamp attached.  It was enough space for me to keep some toiletries, a spare change of clothes or two, my costume and my equipment.  Lisa spent a lot of time talking about what I could do to make the space my own, what I could buy, how I could decorate, but I was happy enough with what we had there.  I kind of liked that it was a bit spartan, because it sort of fit with how I didn't plan to be around that long while still feeling weirdly appreciative at being accepted as a part of the group.



Having tired ourselves out, we'd all collapsed on the couches and watched some of Alec's movies from Earth-Aleph, the alternate Earth that our Earth had been communicating with since Professor Haywire tore a hole between realities.  Media was one of the few things that could be traded back and forth through the hole.  Long story short, you could get books, movies and DVDs of TV shows from the other world, if you were willing to accept the price tag. The benefit? I got to spend the afternoon seeing how the other universe had handled episodes one and two of the Star Wars films.



Fact: they were still pretty disappointing.



By the time my dad got in, I had pork chops defrosted, dusted with lemon and pepper and sitting in a frying pan, with vegetables in the microwave.  Cooking was sort of something you started doing when you had only one parent, unless you really, really liked takeout.



``Heya,'' my dad greeted me, ``Smells good.''



``I started dinner a bit early because I have somewhere I want to be, tonight, If that's cool?''



He tried to hide it, but I could see a bit of disappointment.  ``Of course,'' he said, ``Your new friends?''



I nodded.



``Let me get changed and then I'll ask you all about them,'' he promised as he headed upstairs.



Great.  I hadn't had to answer these questions last night because my dad had been working late.  My mind started racing to anticipate questions and come up with plausible details.  Should I use their real names?  Or at least, the names they had given me?  I wasn't sure if that would be a breach of trust.  I decided to use their real names for much the same reason I'd decided to use my own with them.  It just prevented disasters if my dad ever happened to meet them, which was a terrifying thought, or if they called for me.



I didn't need to worry about my dad hearing about four kids being arrested, all of whom had the same name as my `friends', since most or all of them were minors and their names would be kept from the media under the law.  I was also under the impression that the courts didn't always unmask capes when they arrested them.  I wasn't entirely sure what was up with that.  It seemed like something to ask Lisa about.



By the time my dad had come back downstairs, I'd resolved to try and keep my lies as close to the truth as possible.  It would be easiest to keep everything straight that way.  That, and I hated lying to my dad.



My dad had changed out of his dress shirt and khakis, into a t-shirt and jeans.  He mussed up my hair and then took over the last bit of the cooking.  I sat down at the table so I could talk to him.



``So what's going on?'' he asked.



I shrugged.  I hated feeling this tense around my dad.  He'd never bugged me about the bullying, so I'd always been able to come home and sort of let my guard drop.  I couldn't do that now, because I was just waiting for the other shoe to drop as far as my skipped classes, and my new `friends' brought a whole mess of secrets and lies into the mix as well.  I felt like I was on the verge of a terminal breach of trust.  One mistake or a single concerned phone call from the school, and my dad would probably flip, and things wouldn't be the same between us for a long time.



``Are you going to tell me their names?'' he asked.  He set the food on plates and brought it to the table.



``Brian, Lisa, Alec, Rachel,'' I confessed, ``They're alright.  Get along with most of them.''



``Where did you meet them?  School?''



I shook my head, ``I wanted to get away from school for a bit, so I caught a bus downtown to catch a bit of a break.  I ran into them at the library.''  Partial truths.  You couldn't really catch a bus downtown and back during the lunch break – I'd tried, when I was avoiding the trio – but I doubted my dad would research that.  I did sort of cross paths with the Undersiders at the library, though.



``They go to the library at lunch?  What are they like?''



``Brian's pretty cool.  He's the one I've talked to the most.''



``A boy, eh?'' My dad wiggled his eyebrows at me.



``Dad, stop!  It's not like that,'' I protested.  I doubted Brian had the slightest interest in me, not least because I was two or three years younger than him.  Besides, well, I was me.  I opted not to mention the age difference to my dad.



Changing the subject, I said, ``Lisa's alright too.  Really smart, though I haven't talked to her all that much.  It's nice being able to hang out with another girl again, even if she's pretty different from me.''



``If she's smart, she can't be that much different from you.''



I could've kicked myself.  I couldn't explain she was a bad guy, while I was an aspiring superhero, or exactly how she was `smart'.  I'd talked myself into a minor corner where I didn't have an answer ready, and I needed to avoid doing that.  Fumbling for an answer, I said, ``She's only a year older than me, and she's graduated high school already.''  That was the truth. She cheated, but she did technically graduate.



My dad smiled, ``Impressive.  Tell me they're all excellent students that can serve as good role models for you.''



I could have choked.  Good role models?  Them?  I kept my composure and limited myself to a little smile and a shake of the head, ``Sorry.''



``Alas.  What about the others?''



``Alec is the youngest, I think.  Kinda hard to connect with.  He's an amazing artist, from what I've seen, but I don't really see him draw.  It seems kind of hard to get him interested or involved in anything.  He always looks bored.''  As I said the words aloud, I realized they weren't exactly true.  The two times I'd seen Alec react to anything had been when he'd played his little prank on Brian, tripping him, and after Bitch and I had been fighting.  A streak of schadenfreude to his personality, maybe.



``And the last one?  Rita?  Rachel?''



``Yeah, Rachel.  I don't get along with her.  I don't like her.''



My dad nodded, but didn't say anything.  I was halfway expecting the typical parental line of `maybe if you try to show interest in things she likes' or some other inane advice.  My dad didn't pull that on me, he just took another bite of pork chop.



I elaborated a bit, to fill the silence, ``She wants things her way, and when she doesn't get that, she gets mean.  I dunno.  I get enough of that at school, you know?''



``I know,'' my dad said.  It was a good lead-in for him to question me about what was going on at school, but he didn't take it.  He stayed quiet.



I felt immensely grateful, right then.  My dad was respecting the boundaries I'd set, not pushing, not digging for more.  It made this conversation so much easier that it might otherwise have been, and I knew it couldn't be that easy for him.



I felt like I owed him something for that.  Sighing, I admitted, ``Like, at school.  The, uh, the people who're giving me a hard time?  They sort of ganged up on me on Monday.  Just, you know, taking turns insulting me.  It's why I needed to get away and went downtown.''  I felt embarrassed, saying it, because it was humiliating enough to live through without having to recap it, and because it felt so disconnected from the rest of the conversation.  But if I didn't say it right then, I don't think I would've been able to.



My dad sort of went still.  I could see him compose himself and choose his words before he asked, ``Not to diminish how much it sucks to get put down like that, but they didn't do anything else?''



I raised my eyebrows in question as I chewed.  They had, kind of, but I couldn't really say `They used Mom's death to fuck with my head' without having to explain the Emma thing.



``Anything like what happened in January?'' he asked.



I lowered my eyes to my plate, then shook my head.  After a few moments I said, ``No.  January was a one time thing.  They've pulled smaller `pranks' since then, hassled me, but no repeat performances on that front.''  I made air quotes with my fingers as I said `pranks'.



``Okay,'' my dad said, quietly, ``That's a relief to know.''



I didn't feel like sharing any more.  You'd think I would feel better, after opening up, but I didn't.  I felt frustrated, angry, awkward.  It was a reminder that I couldn't have a real conversation with my dad like I used to be able to.  More than anything, I felt guilty.  Part of the guilt was because I'd apparently let my dad think that every time I was bullied, it was like it had been that day, nearly four months ago, when things had been at their worst.  I stabbed at a bit of fat with my fork.



``When were you going out?'' My dad asked.  I glanced at the digital clock on the stove and noted the time.



I was glad for the excuse to escape, ``Now?  Is that okay?  I won't be long.''



``Meeting your friends?'' he asked.



``Just going to meet Lisa for coffee and conversation, away from the rest of the group,'' I told him as I stood up and moved my plate to the sink.  The lie was heavier on my conscience after the open disclosure I'd just had with him.



``Here, wait,'' he said.  He stood up and fished in his pocket for his wallet.  He handed me a ten, ``For the coffee.  Sorry I don't have more.  Have fun?''



I hugged him, feeling painfully guilty, then headed to the back door to pull my shoes on.  I was just opening the door when I barely heard him say, ``Thank you.''



``Love you, Dad.''



``I love you too.  Be safe.''



I shut the door, grabbed the gym bag I'd stashed under the back steps and headed around the house at a light jog.  I held the gym bag low so my dad wouldn't see me carrying it.



I took the same general route I took on my morning runs, heading east, towards the Bay.  This time, though, instead of turning up towards the Boardwalk, I headed south.



Back in its heyday, every inch of the city had been a bustling metropolis.  Ships were coming and going at all hours, trains were coming through to deliver goods to be shipped overseas and the city teemed with people.  The northern end of the bay – especially the area close to the water – was all about the industry.  Ships, warehouses, factories, railroad and the homes for everyone who worked those jobs.  You also had the ferry running across the bay itself.



The ferry was my dad's pet project.  Apparently, it had been one of the first things to go when the import/export dried up.  With the ferry gone, the Docks had sort of been cut off from the rest of the city, unless you were willing to drive for an extra half hour to an hour.  My dad held the opinion that the lack of that transportation to the rest of the city was why the Docks had become what they were today.  He believed that if the ferry were to start running  again, jobs would be created, the people in the low income neighborhoods would have more access to the rest of the city, and the low-class, high-class, no-middle-class dynamic of Brockton Bay would smooth out.



So when I'd been trying to think of a place that was fairly private but easy to find, I thought of the ferry.  I could probably thank my dad for the idea.



I approached the station and found a disused restroom to change into my costume.



The building and the ferry itself were well kept, at least on the outside, which was one of the reasons my dad felt it would take so little effort to get things going again.  Still, that wasn't the city's issue.  They didn't want to provide the addicts and the gangbangers easy access to to the rest of the city, all the while paying to provide the service, for mere hopes of \emph{maybe} getting improvements for the future.  So the city kept the station and the ferry looking pretty for any tourists that wandered far enough south from the Boardwalk and maintained eternal `temporarily out of service' and `coming soon' signs up around the building and in the brochures.  Aside from the regular replacements to keep them looking new, the signs hadn't been taken down in nearly a decade.



I ignored the doors to the station's interior, and instead headed up the stairs to the outdoor patio that overlooked the bay.  There were some large panes of glass to break the wind, and stone tables and benches for those wanting to sit to eat.  It was one of the best vantage points for seeing the PHQ in all its splendor.  The headquarters was a series of arches and spires mounted on a retrofitted oil rig.  Even the platform it was built on was beautiful, though, with hard edges and sweeping lines.  The entire thing was lit up by tinted spotlights and set against a faint corona of shifting colors, like the aurora borealis trapped in the shape of a soap bubble.  A forcefield, forever on, shielding the people who watched over Brockton Bay.



``Wasn't sure if you would show up,'' a male voice broke the silence.



I turned to face Armsmaster, ``I'm sorry.  I had to hang up on your receptionist.  Real life called.''



He looked somehow different than the first time I'd met him.  His lips were set in a hard line, his feet set further apart.  His arms were folded across his chest with his Halberd in one hand, the pole resting against his shoulder.  It conveyed such a different attitude that I momentarily wondered if he was the same person under the suit.



``I need to call in a favor.''





