





``A favor,'' he answered me, as if he needed to say it out loud to himself to believe it.  The tone gave me pause.  Had I misread him, that first night, when I gave him credit for Lung and assumed he was grateful?



``Yeah,'' I tried to sound confident, ``But I should explain things first.  First off, the Undersiders offered me a spot on their team.  I took it.''



His reaction was subtle.  His chin rose a fraction, he shifted his weight fractionally, and  the grip of his armored gauntlets tightened enough on his Halberd to make a faint metal-on-metal screech.



``I think you'd better start making sense, fast,'' he spoke in a calm voice, even as his body language was making me want to back away.



I took a deep breath, trying to calm my nerves, ``I've been thinking a fair bit about the conversation we had last Sunday.  It seemed odd how you accepted I was a good guy as fast as you did.  Would I be right in guessing you either have a lie detector built into your helmet or some power that works more or less the same way?''



He didn't hurry to give me a reply, taking a few moments before telling me, ``Lie detectors can be fooled, even mine.''



``Well, tell me if anything sets an alarm ringing, or if your instincts tell you I'm lying.  I was a good guy then, I'm a good guy now.  I joined the Undersiders because you said you were having trouble getting info on the guys.  Now I know their faces, I know the names they're using, I have a pretty good idea about what their powers do, and I know where they're living.''



His posture relaxed.  He slapped the pole of his Halberd against his back and it snapped into place.  ``If that's the case, then you've done us a great service.  Would you be willing to come to the Protectorate Headquarters and present that information to the team?''



My heart leapt.  Meeting the local Protectorate, with Miss Militia, Triumph, Velocity, Dauntless, Battery and Assault?  I could imagine seeing their reactions to everything I'd found, telling them about my fight with Bitch, maybe about my part in the fight with Lung, if Armsmaster was cool with that.  Hearing their stories in turn.



``I can't.''



``Why not?'' his response was so quick it was very nearly an interruption.  His tone and posture were both hostile again in a flash.  I was glad he wasn't still holding his Halberd, because I think he might have pointed it at me.



``There's one more thing I need to find out for you,'' I said, raising my hands in a sort of surrender.  I needed to find out who their boss was.  I couldn't tell him that, though.  The less he knew, the less likely Tattletale would know I told him anything.  At least, I was hoping that was the case.



``So tell me what you know and then go find that last detail.''



``I can't,'' I answered for the second time in ten seconds, hating myself for doing it.



``You'd better have a good reason, or I'm dragging you to the PHQ and we'll see how well you tease when you're in front of the entire team.''



Which would be a disaster.  I swallowed hard, ``What if I told you there was a spy in the PHQ?''



``You'd be setting off the lie detector.  Try again.''



I bit my lip.  I'd been hoping that phrasing it as a question would throw it off.



``There's something at play that's for all intents and purposes, a spy in your ranks.''



``Mostly true.  What is it?''



``I can't be any clearer without them figuring out I told.  Just my being here is really risky.''  If word got out as to how Lisa's power worked, I was almost positive she'd know how.



He stared at me for several long moments, ``The Tattletale girl.''



Armsmaster had come to the conclusion more or less on his own.  I hoped that was enough to keep Tattletale from drawing a connection to me.  Still\ldots fuck.



He stared off towards the PHQ for a few long moments.  Without looking at me, he asked, ``So you're not willing to provide any concrete information.  Why did you call me?''



``They're planning something.  They want me to help them.  I do this, maybe one or two other jobs, I'm sure I can get that last essential detail, and you'll have what you need to capture these guys.''



He didn't reply.



So I asked my favor, ``I need to know that if things go sour or if I need to sabotage their plan, I'll have you to pull my ass out of the fire and keep me out of jail.''



``What are they planning?''



``I can't say,'' I admitted.  If I told him, Lisa might know I'd ratted the team out from any changes in the response time, extra guards or whatever else.  However justified my silence was, I could see Armsmaster getting increasingly irritated.



``Is it murder?  Is someone going to get hurt?''



``No,'' I said, ``I'm pretty sure no civilians are going to get hurt, unless things go really wrong, which is something I'm hoping to prevent.''



He frowned, then stopped gazing out the window to look straight at me. ``I'm not giving you any protection.''



I clenched my fists at my sides, ``This is the only thing I need, and you've got them!''



``You're a stupid girl,'' Armsmaster said.  He gave me a moment to let the words sink in.



``I--''



He didn't give me a chance to speak.  He bowled over me, his voice rising as he spoke, ``You're asking for my permission to carry out a major crime.  At least, I assume it's a major crime, because you wouldn't be asking otherwise!  You want me to stand by so you can play your little spy game with a team that has two murderers on it!''



Two?  I could believe that Rachel had maybe killed someone at some point, manslaughter if nothing else, but who else would?  Eyes wide, I asked him, ``Who--''



I didn't get to finish my question.  Armsmaster talked over me until I shut my mouth and listened.  ``Do you think you're clever?  In the real world, undercover cops have handlers.  They have someone to report to, someone that can call in backup at any time.  You?  You're a middle schooler with delusions of grandeur.''



``I'm not in middle school.''



``Oh, well,'' he crossed his arms, ``I stand corrected on all counts.'' The sarcasm in his voice was palpable.



I protested, ``And if I did have back-up or a handler or anything like that, they'd \emph{know}.  The way I'm doing this is the only way this could work.  Use your lie detector, you'll know I'm telling the truth about this.''



``I know you \emph{believe} you're right.  That doesn't make it god's honest truth.''



There was something about hearing all this from Armsmaster that made it twice as hard to take.  I opened my mouth, but my brain just couldn't piece together a coherent response.  I shut my mouth again.



``Abandon this charade, little bug girl, before you bite off more than you can chew.  Tell me what you know, right now, then go home.  I don't care if you put your costume away for good or if you sign up for the Wards, but don't go on with the solo act.  That's my recommendation.''



That stung.  I tried again, ``I gave you Lung, full credit.  You can't give me the benefit of a doubt?''



``You gave me a dying man!'' Armsmaster bellowed, startling me, ``That was on my shoulders!  I had to put up with two days of losing command of my team, two days where they confiscated my Halberd and power armor!  I was interrogated, all my equipment taken apart and checked!  All because \emph{you} couldn't resist using your bugs to give that man a fucking near-lethal dose of poisons!''



His attitude from the beginning of this meeting had been hostile.  Now I understood why.  I held my ground.



``That's not my fault,'' I told Armsmaster, my voice strained with anger.  I gave voice to a suspicion that had been nagging at the edge of my consciousness since I'd heard about Lung being hospitalized, ``I didn't dose him with enough venom to kill him.  What \emph{I} think is that the tranquilizers that you pumped into his system knocked out his ability to heal, which is what let the poisons do as much damage as they did.''



We glared at each other, as much as people can exchange glares when they can't see one another's eyes.  Still, it wasn't hard to imagine the expression on his face.



``If you contact me again, you'd better be prepared to answer every question I have.  Beyond that, I'm not condoning anything about what you're trying to pull.  You're on your own.''



I would have been happy to storm off, or offer my own angry parting words.  Except there was something else I needed from him.  On the assumption that he'd take me up on my offer, I thought I'd ask as a last, minor favor.  Now I was put in a situation where I might have to beg a man I really wanted to punch in the face.



``I--'' I paused, trying to find the words, ``I'm asking you to please not tell anyone we met tonight.  No records, on paper or computer.  Don't do anything different because of what you learned tonight.  I know I can't make you.  I don't have anything to offer you, besides the information I'm going to get.  But if these guys get wind that I met you, it's going to go really badly for me.''



``You made your bed.  You have to lie in it.''



``No,'' I shook my head, furious he was being so mule headed.  My fists clenched, ``Don't toy with me here.  Maybe you don't agree with what I'm doing, but I started this because I wanted to do \emph{you} a favor.  The least you could do is not screw with me on this, and get me hurt or killed because your fucking rep got a smudge on it.''



I regretted my words as soon as they left my mouth, but I could hardly take them back.



``Fine,'' he decided, then dismissed me, ``You can go, now.''



It was a dick move, that last bit, because I was following his order if I listened and it made me look bad if I didn't.  Still, if there was any upside to the bullying I'd endured out of costume, it was that I could handle the little maneuvers of bullies and assholes when I was in costume, too.  I left and didn't think twice about it.



I was pissed, and it was a lot easier to be pissed at Armsmaster than it was to be angry with myself.  This hadn't gone the way I'd planned.  I didn't even know if that `fine' of his was an agreement to do as I'd asked, or if I was royally screwed the next time I went to meet with the Undersiders.  There were two ways I could respond to this.  I could either drop the plan and put away my costume like Armsmaster wanted, or I could pull off the undercover gig and prove him wrong.



Fuck it.  I was going to rob the hell out of that bank.  I'd win the trust of the Undersiders, I was going to figure out who was running the show, and then I was going to hand over all of the info.



To Miss Militia, I was thinking.  Not Armsmaster.

















