





``Think of it as a game,'' Lisa said, ``A high stakes variant of cops and robbers.''



A steady downpour of rain thrummed against the outside of the van Lisa was driving.  The rain drowned out all other noise of the traffic around us and muted our view of the surroundings, making the interior of the car an island in the midst of downtown.  Traffic was at a deadlock, so bad that Lisa had put the van into park and turned off the engine.  To break the silence, I had asked Lisa why some villains didn't get their secret identities revealed when they got caught, and I'd apparently stumbled into one of her favorite topics.  I supposed it was good that she was in a mood to talk, because I wasn't.



``I think,'' I ventured, ``That it's a little closer to real cops and robbers than the schoolyard game.''



``No, no.  Hear me out.  Grown adults running around in costume?  Making up code names for themselves?  It's ridiculous, and we know it's ridiculous, even if we don't admit it out loud.  So there's capes like you and me, where we go out in costume and it's fun.  Maybe we have some agenda or goals, but at the end of the day, we're getting our thrills, blowing off steam and living a second life.  Then there's the crazies.  The people who are fucked up in the head, maybe dangerous if there's not something or someone to help keep them in line.  The people who take it all too seriously, or those guys you wouldn't want to get on the wrong side of, even if they didn't have powers.  Lung, Oni Lee, Heartbreaker,'' she paused.  ``Bitch.''



I nodded.



``And there's the monsters.  The really dangerous motherfuckers, who are barely human any more, if at all.  The Slaughterhouse Nine, Nilbog--''



``The Endbringers,'' I interjected.



Lisa paused, ``Right.  But you have to understand, ninety percent of what goes on when you're in costume?  It's the first group.  Adults in costumes playing full contact cops and robbers with fun-as-fuck superpowers and toys.  This mindset applies to the people without powers too.  Way I see it, having a local team of superheroes is like having a sports team.  Everyone's rooting for them, they make for great media that isn't about wars or the water crisis or whatever, there's merchandising and tourists\ldots all good shit that the local government loves.  But what good is having a team if there's no competition?''



``Which is where we come in,'' I figured out where she was going.



``Exactly.  At the end of the day?  We're not doing much harm.  Property damage, theft.  A few civilians get hurt if they don't move out of the way fast enough.  But insurance payouts cover that stuff, and people aren't that much worse off.  The property damage is covered and the injured bystander has a great story to tell at the water cooler.  The city gets revenue in an indirect way, from merchandise, tourism and the rising property that come with being an exciting city.



``Compared to the psychos and the monsters out there, it's almost in the city's interests to keep us in circulation.  Far as I see it, we're not that much better or worse than the so called good guys.  We face more risk at the end of the day, with the possibility of jail time and physical danger, but we get a better payoff.  We just took the path that was higher risk, higher reward.''



``I'm not sure,'' I said, carefully, ``That I buy all that.''



``No? Then why don't they send people like \"{U}ber straight to the Birdcage after his trial, like they are with Lung?  The amusing but relatively harmless villains get a regular jail cell, they inevitably break out before the trial concludes, and the cat and mouse game starts again.  Sure, there's the three strike rule, and he'll get sent to the Birdcage eventually, but the people in charge have to maintain \emph{some} plausible deniability.''



I didn't think there was a way I could argue against Lisa's theory without giving too much of my own perspective away.  I just kept my mouth shut and turned my new knife over in my hands.  Direct from our anonymous `boss', it sported a blade a little over six inches long and a textured handle with three symmetrical indents on each side, for grip.  According to Lisa, it was strong enough to use as a miniature crowbar, if I had a mind to.  My extendable combat baton was tucked away in the panel of my armor where I kept my pepper spray.



``But the real evidence to my `cops and robbers' theory,'' Lisa continued, ``Is the reaction you see when someone crosses the line.  You've heard about it happening.  Someone finds out another cape's secret identity, goes after the cape's family.  Or a cape wins a fight and decides his downed opponent isn't in a state to say no if he's feeling lusty?  Word gets around, and the cape community goes after the fucker.  Protecting the status quo, keeping the game afloat.  Bitter enemies call a truce, everyone bands together, favors get called in and everyone does their damndest to put the asshole down.''



``Like we do with the Endbringers,'' I said.  I sheathed my knife.



``Holy fuck,'' Lisa said, slapping the sides of the steering wheel with her hands.  I think if the van had been moving, she would have hit the brakes for emphasis.  Traffic was starting to move, though, so she started up the car and put it into gear, ``Twice, you bring up the Endbringers in as many minutes.  You're being morbid.  What's going on?''



I stared out the window at downtown Brockton Bay, hundreds of people with umbrellas and raincoats, a few intrepid individuals bolting down the street with a briefcase or newspaper over their head, to ward off the downpour as they made their way to or from their work on their lunch hours.



It was hard to talk to Lisa, as much as I liked her as a person.  I felt like I was walking on eggshells.  If I said something, would that give her the puzzle piece she needed to figure me out?  I had been lucky so far, but relying on luck sucked.  I was counting on this ruse continuing, whether it was because I enjoyed the temporary companionship of Brian, Lisa and Alec, or because I wanted to get Grue, Tattletale, Regent and Bitch carted off to jail and prove Armsmaster wrong.  I \emph{was} aware how paradoxical those two interests were.



But right now, maybe for the first time since Bitch had set her dogs on me, I felt painfully out of place in the group dynamic.  We were robbing a bank, and I was the only one who was guilty about it, apparently the only one who was worried about the safety of the bystanders and hostages.



Then there was the fact that Armsmaster had said that \emph{two} members of the Undersiders were murderers, and doubt was tainting every interaction I had with these guys.  When I was smiling about a joke Alec made, was I enjoying the joke of a killer?  I liked Brian, but now I was looking back on how he had pointed out how to brutally disable someone in a fight, and I was wondering if he'd ever gone that one step further and snapped someone's neck.  It wasn't a hundred percent impossible to imagine that one of the secrets Lisa was so fond of keeping included murder, either.  I felt like every interaction with these guys was spoiled, now, and there was nobody I could ask to clarify the lingering questions.



Still, staying quiet now would only make her more suspicious, and if she turned the full extent of her power on me, I doubted my undercover ruse would withstand her attention.  I confessed with a half truth, ``I got in an argument with someone last night.  I think it was mutual disappointment, got pretty heated, hurtful.  I guess I'm a bit angry, and my confidence is a little shaken.''



``Well, fuck them,'' Lisa stated.  I raised an eyebrow in response.



She went on, ``See, I know you.  Believe it or not, I \emph{like} you.  Did from the time I saw you on that roof, opposite \emph{Lung}.  You know how we fear the unknown?  Well, I \emph{know} stuff, that's my whole thing, and that motherfucker is one of the very few people who can spook me.  You, Taylor, stood up to him.''



In a manner of speaking, anyways.  The way I remembered it, I'd been curled up in a fetal position when the Undersiders came to my rescue.  I didn't correct her.



``So this guy or this girl that's got you down in the dumps?  I say fuck them.  They don't know you.  They don't know what you're capable of.''



I would have stopped myself if I could have, but the irony of her statement was too rich.  I grinned, looking out the window to hide the expression from Lisa.



``I saw that.  Don't think I didn't.  So I've shaken the doldrums from you.  Good.  Now look to our left.''



``Who uses words like doldrums, anymore?'' I voiced my thoughts as I obeyed her instruction.  She only chuckled in response.



As I realized what I was looking at, through the rain and the past the traffic, I swallowed hard.  It was a stone fixture six stories tall, with crenelations on the roof and balconies, stone gargoyles at the corners and iron grilles on the windows. The entryway had wide stone stairs like a courthouse, with statues of rearing horses with wild manes on either side.  The name of the institution was etched into the stone above the doors.  The Brockton Bay Central Bank.  A virtual castle.



``In twenty minutes or so, we're going to be leaving there, tens of thousands of dollars richer, the adrenaline rush of victory pumping through our veins,'' Lisa's voice was barely above a whisper, ``Now tell me.  Can you visualize that?''



Not really.



``Yes,'' I tried.



``Liar,'' she said.  Then she winked at me, ``It's okay.  An hour from now, you'll be rolling in money and laughing about how pessimistic you were.  Promise.''



Lisa pulled the van around to circle the block, then pulled into an employee parking lot behind a restaurant.  As she pulled into the parking lot, bringing us right to the back corner of the bank,  I pulled on my mask.  Lisa did the same, then took a few seconds to smear her eyelids with black facepaint so they blended in with her mask.  I wasn't so lucky as to have any final touches to apply, so I watched the rearview mirror nervously.  It felt like an eternity, but was probably closer to a minute, before Brian pulled a second van into the alley that led into the lot.  He parked his van halfway down the alley, blocking anyone else from coming through.



As I opened the car door and hopped out into the pouring rain, I managed to say the words without choking on them, ``Let's go rob a bank.''



Lisa grinned.

















