





Grue was already out of his vehicle and halfway to us by the time Tattletale and I had shut the doors of the van.  He was using his power at a low degree over the entirety of his body.  The darkness soaked into and through the porous leather of his costume, making him look like a living shadow.  Brian had showed me how the visor had vents at the edges, to direct the effect of his power around the sides and top of his head, so it wouldn't obscure the face.  It wasn't that he couldn't see through the effects of his own power – he could.  He'd explained that the vents were there to create an effect where you could see glimpses of a black-painted skull floating in the vaguely human shaped form of even darker black.  When he had the money to spend, he had told me, he was going to get a more complete costume custom made for him in the same way, to expand on the effect.



``Let's move fast.''  His voice echoed, reverberated, with a hollowness to the sound, like something alien and far away.  He was using his power to play with the sound, ``Tattletale, see to the door.  Bug, with me.''



Together with Grue, I returned to the van Lisa had been driving.  Grue grabbed the handle of the sliding door and hauled it open, then scrambled out of the way as the contents came pouring out.



I chuckled at the image of this spooky supervillain being caught off guard.  I'd packed the entirety of the van, minus the driver and passenger seats, with bugs.  As the door opened, they spilled out to pool on the wet pavement beneath the door.



``Got enough?'' his voice echoed.  I thought maybe I caught a touch of humor in his tone, behind the influence of his power.



I smiled behind my mask, ``Let's hope.''



A drive earlier in the morning had given me the opportunity to gather this swarm.   It was surprising how many bugs there were in the city, hidden from sight.  At any given point in the city, I could generally draw out tens of thousands of bugs from inside walls, sewers, attics, lawns, trees and even places you would think were too clean or occupied to have any creepy crawlies lurking about, and I could do it over a matter of minutes.



These weren't just the bugs I could draw in at a moment's notice, though.  Traveling the city had given me the chance to be picky.  These were the good ones, each of them fast enough to keep up with me, or capable of being carried by those that were.  More than that, though, the majority of them were either durable sorts like the larger centipedes, cockroaches and beetles, or capable of stinging and biting, with bees, wasps, ants and blackflies making up their bulk.  To round out their number, I'd gathered moths, houseflies, and mosquitoes, who weren't the best attack bugs out there, but were easy enough to get, and served to distract the enemy or bulk out the swarm.



There were three hundred and fifty cubic feet inside the rear of the van. Tattletale had told me that.  When they were packed in just tight enough that they wouldn't damage each other or spill past the barrier and into the front seats, it added up to a pretty amazing amount of insects.  I called them out of the van and watched as their mass seemed to expand as they spread out.



We joined Tattletale at the side door of the bank. I had to admit, I admired the sheer change she was capable of pulling off when donning her costume.  Rather, I should say, I admired the effort she'd gone into as Lisa, that made her so different from her Tattletale persona.  Her mask was narrow, only really surrounding her eye sockets, covering her eyebrows, some of her nose and some of her cheekbones, but it hid the freckles on the bridge of her nose and changed the apparent lines of her face.  Her hair was down and loose, damp from the rain, in contrast to how it was always in a ponytail or braided when she was `Lisa'.  Her costume was skintight, beaded with droplets of water, lavender with bands of black across the chest and down the sides of her arms, legs and body.  An image of a stylized eye, only visible in the right light, given it was dark gray on black, was worked into the costume's design.  A compact `utility belt' sat diagonally across her hips, sporting a variety of compact pockets and pouches.



Regent was keeping watch, a few feet away.  From what I'd seen while we prepared, I now knew his costume was deceptive.  He still wore the hard white mask with the silver coronet, but he had shown me how the interior of the mask had foam shaped to the contours of his face, with only his mouth left free, so he could talk without being muffled.  In a similar vein, the loose white shirt he wore covered up a mesh vest that was molded to the shape of his body.  He was idly twirling a scepter in his fingers.  The scepter wasn't purely thematic – apparently the crowned orb that topped the scepter had two electrodes built into the tines, for the taser that was built into it.  It was all about misdirection, misleading and giving the impression of vulnerability.



``The fire exit at the back is protected by a digital passkey,'' Tattletale explained while she crouched at the keypad, staring at it, ``Every employee has the number to get in if they need to, but that rarely happens because opening the door sets off a bunch of alarms.  That password is easy.  The interesting thing that the employees don't even know is that the capes and SWAT teams have a special code they can put in if they need to make a quiet entrance with no alarms going off.  To do \emph{that}, you punch in the regular code, 3-7-1, but you hold the one down, then press the number sign and the asterisk keys down at the same time\ldots Voila.  Try it.''



Grue pulled on the door.  We waited in tense silence for a moment for the angry blare of the alarm, but none came.  Tattletale grinned at us. ``What'd I tell you?''



Grue signaled, and we were joined by Regent and Bitch with her three dogs.  The animals were the size of small ponies, their flesh having swelled and expanded enough that their fur had split at the seams.  Muscle and bone showed beneath, and the arrangement of said anatomy wasn't exactly typical.  The change was slow enough that you couldn't see it if you were looking for it, but if you looked away and looked back a moment later, you could tell they were bigger, that bone at the shoulder was longer, the eyes were deeper set, and so on.  Spikes, spurs and an exoskeleton of bone growths had appeared to fill or cover gaps and grow in at places where the bone was already close to the skin.  The tail of the smallest dog – Angelica, I think Rachel called it – was twice as long as normal and prehensile, now, and the other two were well on their way.  It looked like someone had torn out a pair of human spines, the meat still hanging off them, and attached them one to the other before tacking the end to the dog's hindquarters.



Bitch, for her part, was just wearing a jacket with a fur ruff collar and a cheap, hard plastic mask of a bulldog.  The dogs had been given the rear of the second van, allowing Bitch to work her power on them as Brian drove.  Being able to do the change more slowly meant she wouldn't prematurely exhaust herself or the animals by rushing the job on site.



We made our way into the back hallways of the bank's ground floor, Bitch's dogs leading the way, my swarm pulling up the rear.  The clock had started running down from the moment we'd parked in the alleyway; that was the point where people might have thought something was up.  Now that we were inside, though, \emph{someone} knew, or would know any second.



At this very moment, chances were, some guard in the room with the security cameras would be making a call to 911 and reporting a crime in progress by costumed criminals.  If Tattletale was right, the Protectorate was too far away to be called in, so they would contact the Wards.  We had five or ten minutes before trouble showed.



Each time we passed a room, Grue, Regent and I would double check it.  The first few were empty, but as we reached one room, a dog took notice, and Grue raised a hand to plunge the room into darkness.  A second later, he stepped back into the hallway, twisting the arm of a cringing thirty-something man in a gray suit behind his back.  I hadn't even realized Grue had entered the room in the first place.



In the next room, Regent grabbed another hostage.  I caught a glance of the man, graying hair and thick around the middle with a pink dress shirt and no jacket, staring at us with eyes wide.  He opened his mouth, I think his intent was to cry for help, but broke down into coughs and sputters instead.  A second later, he keeled over and collapsed onto the floor.  He tried to climb to his feet, but his elbow buckled and he hit the ground a second time.  While he continued to struggle, Regent strode into the room with an almost lazy air, grabbed him by the collar and shoved him towards the hallway where we stood.  Defeated, Pink-shirt didn't resist, half-walking, half-crawling forward as he joined us.  He met eyes with the other employee, but didn't say anything.



We only passed a dozen offices, but it felt like three times that number.  Grue was on point, glancing into each room and watching for danger from up ahead, with Regent keeping an eye on rooms to our right.  That meant I was paying attention to the rooms on the left, as well as keeping an eye out by way of the swarm to our rear.  Each time I looked into an office, lunchroom or conference room, I prayed it would be empty.  I didn't want to be any more responsible for all this than I had to.



When I saw the last office on the left was vacant, I was relieved enough that I nearly forgot my role in the next stage of the plan.



We reached the front lobby of the bank, and Bitch's dogs charged into the room.  They were nightmarish, barking, growling and shaking themselves in a spray of bits of fur and blood as they abruptly grew another foot taller at the shoulder.  I had a moment's glimpse of twenty or thirty bystanders and another six or so employees of the bank before the lights went out.  Grue used his power, and the room was plunged into darkness, the volume of the screams and wails dropping to utter silence in a matter of seconds.  We stood in the entryway to the lobby, and there was only nothingness where the bank lobby had been.



``Your move, Bug girl,'' Tattletale said, reaching forward to put a hand on my shoulder.



I closed my eyes.  With a mental command, my bugs flooded into the room from the hallway behind us, flying and crawling over, under and around us to spread through the room.  I noted each person in the lobby as my bugs made contact with them, and left several bugs crawling on each individual.  I took five seconds to double check I'd gotten everyone, and belatedly remembered the two employees we had brought forward from the back offices.  A group of bugs returned from the darkness, brushing my skin on their way to make contact with the pair.



``Done,'' I said.



Grue swept his arms forward, and the darkness parted.  We moved into the room as a group.  Pink-shirt and the younger guy collapsed to the ground as we walked.  I supposed it was Regent's work there.  Some of Grue's darkness clung to the surfaces of the doors and the windows, but the room was otherwise clear in a matter of moments, lit only by the florescent lights.  Everyone except for us was lying on the floor, crouched behind a desk, or huddled in the corners.  Two of Bitch's dogs were standing in front of the main entrance, while the smallest was standing near the vault.  All three of the monsters were the size of cars, now.



``Fifteen minutes,'' I called out to the room, my heart in my throat, ``We won't be here any longer than that.  Stay put, stay quiet, we'll be gone before fifteen minutes are up.  You'll be free to give your statement to the police and then go about your day as usual.  This isn't a TV show, this isn't a movie.  If you're thinking about being a hero, don't.  You'll only get yourself or someone else hurt.''



I held up my hand, finger outstretched, a familiar spider perched on the tip, ``If you are thinking about running, making a phone call or getting in our way, this is a good reason to reconsider.  This little creature and her one hundred sisters that I just brought into this room are under my complete control.''  I had the spider drop from my fingertip, dangling by a thread, by way of demonstration.



``She's a black widow spider.  A single bite has been known to kill a full grown human, or put them into a coma.  You move, talk, try to find or kill the spiders I just put on your bodies, in your clothes, in your hair?  I'll know in split second, and I'll tell them to bite you \emph{several} times.''



I stopped to let that sink in.  I looked over the room.  Forty or so people.  I saw a full grown man with a tear rolling down his cheek.  A teenager with freckles and brown curls was glaring at me with raw loathing in her eyes.  At one of the counters, a matronly bank employee was shaking like a leaf.



My taking hostages like this?  It had been my idea, so help me.  As horrible as it was, it had been necessary.  The worst case scenario was some regular schmuck in the bank pulling some stunt and getting themselves or others hurt or killed.  I couldn't let that happen, if I was in a position to help it.  If it meant keeping them quiet and out of the way, I was willing to terrorize them.



As I saw the effect I'd had on these people, that justification felt really thin.



I was going to hell for this.

















