





``Any trouble?'' Grue asked Tattletale.



``We're okay for now.''



We'd gone over the plan until I'd been worried I would start murmuring about it in my sleep. I joined Tattletale, Grue, Bitch and the largest of the three dogs as we headed to the sealed vault door.  Regent watched at the front doors with the two other dogs.  His power had a good enough range that he could delay any approaching opposition long enough for us to get into position.



Tattletale took hold of the stainless steel wheel that jutted out from the front of the vault and spun it, then stopped it. She repeated the process, going right, then left, then right again, for an indeterminably long time.  Just when I had the hopeful thought that maybe she wasn't able to get in, there was a sound of something heavy shifting inside the door.



The four of us hauled the door open, and Tattletale sauntered off to where the bank manager worked. She sat herself down at the computer, putting her feet up on the corner of the desk, and began typing away.  From there, she could keep an eye on the media, watch the surveillance cameras and remotely control the door locks and alarm systems.  All with the right passwords, of course, but that wasn't a problem for her.



Grue, Bitch and I started strapping a canvas harness onto the one dog that wasn't standing at the front doors. I was gradually working out which was which.  I think Bitch called this one Brutus.  He was the biggest, with the meatiest body, and he had a shorter snout.  He'd been the Rottweiler, before.



He turned his massive head towards me, until the deep set eyeball was just to the left of my head.  The pupil narrowed into a dot.  There was just the bloodshot white of the eye and the yellow-gray of an iris as broad as my handspan.



I knew the worst thing to do would be to show fear or nervousness, so I was careful to breathe slowly and focus on buckling the straps and making triply sure they were fastened tight.  I was maybe being a little too firm, just to ensure the Brutus didn't think I was weak or shy.  Not that it mattered.  I seriously doubted I could make him flinch, even with one of my weapons in hand.



With the harness securely fastened, we headed into the vault, Brutus standing at the door.  The vault was stainless steel from top to bottom with neatly banded bundles of bills organized into stacks.  The stacks, in turn, were organized by the size of the bill, all neatly set up against the wall. On the wall opposite the stacks were drawers like an elaborate filing cabinet.  They were pretty much just that.  The bank kept copies of all important documents for the local branches here, in a fireproof vault, in case of disaster.  The far end of the vault had another door, opening into an elevator that went down to the garage basement, where the armored trucks could be loaded.  It was a shame it wasn't an option for an escape route. The door, the elevator and the garage itself were all firmly locked outside of specific times and days.



Bitch dumped an armload of bags onto the ground, and she and I got on our knees on either side of the pile and began stuffing one of the bags with cash.  She took off her mask to see what she was doing better.  Grue, for his part, withdrew a short crowbar from within the darkness that smoldered around his body.  He set to cracking open the filing drawers with the squealing noise of metal creaking and bending.



As Bitch and I filled the first bag, we buckled it closed, cinched the accompanying strap tight around it, and with mutual effort, slid it across the slick metal floor towards Brutus. Grue turned away from the drawers to grab the bag, haul it up and attach it to the dog's harness.



It was a staggering amount of money. As Bitch and I worked, I started trying to count the money I was putting into the bag. Five hundred, one thousand, one thousand five hundred. Bitch was working just as fast as I was, so I could double that. Just taking a second to wrap my head around what the total amount would be per bag made me lose track.



We filled a second bag and slid it towards the door. Grue grunted as he heaved it up to the opposite side of the first bag and clipped it in place. While we filled the third bag, he clipped on one more – a bag filled with the contents of the first drawer he had opened.  According to Lisa's briefing, the drawers would hold deeds, liens, insurance forms, mortgages and loan information.  Apparently our employer was willing to buy these from us.  I'd speculated about why – the most obvious possibility was that he could ransom them back to the bank.  More intriguing was the thought that he wanted the information itself for his own purposes.  Or, on a similar note, maybe there was something specific that would be found in the midst of the paperwork, and he was willing to buy it all if it meant keeping his true intentions unclear.



``I'm going to be sore tomorrow,'' Grue groaned, as he recovered from strapping the bag of papers into place, ``And we haven't even been in a fight yet.''



``Sore and rich,'' Bitch spoke.  I glanced at her and saw her grinning.  It was disquieting.  I'd only ever seen her sullen and hostile, so any smile would be kind of creepy.  It was worse than that.  Hers was the kind of smile you'd see from someone who had never seen one before and was trying to replicate one from what they'd read in books.  Too many teeth showing, I suppressed a shiver and focused on the work.



We slid the third bag across the floor.  Grue hooked it into the harness.



``We can't put any more on here without it being a problem,'' he decided.



``The weight is even?'' Bitch asked.



``Close enough.''



Bitch stood and crossed the length of the vault to where her creature waited. She rubbed her hand on Brutus' snout like you might see a horse owner do, except Brutus most definitely wasn't a horse. She was rubbing her hand on exposed muscle, calcified tatters of flesh and bone hooks that jutted out of gaps and knots in the muscle. She managed to look almost affectionate as she did it.



``Go, baby. Go,'' she commanded, pointing to the front door. Brutus obediently loped off to the front of the bank and sat, his prehensile tail absently coiling around the door handle.



``Hey!'' Bitch called out, then whistled twice, alternating between short and long. The smallest of the dogs, who was only recognizable now by her missing eye, bounded towards us in her excitement. Some of the hostages screamed in alarm at the sudden movement.



I winced.  I didn't want to think about the hostages. They were already heavy on my conscience, and they were constantly on the periphery of my attention, as long as I continued using the bugs I'd planted on them to keep alert for any movement or talking.



``That's the one you call Angelica?'' I asked, to distract myself. ``The name doesn't seem to fit with what you call the others.''



``I didn't name her,'' Bitch said. As the creature approached her, Bitch slapped her a few times on the shoulder, hard. It didn't hurt the animal though – Angelica just lashed her tail in what I realized was a warped way of wagging her tail. Bitch snapped her fingers twice and pointed at the ground, and Angelica sat.



I had already partially filled a bag when Bitch rejoined me.



``She had previous owners then.''



``Fuckers,'' Bitch swore.



``They were the ones who made her lose her ear and her eye?'' I asked.



``What? You think I fucking did it?''  She dropped the money she had in her and and stood up, clenching her fists.



``Woah, no,'' I protested, shifting my weight so I could move out of the way if she got aggressive, ``Just trying to make small talk.''



She took a step toward me.  ``Coward.  You know you can't take me in a-''



``Enough!'' Grue shouted.  Bitch turned on him, her eyes narrowing.



``If you can't work over there, then take over here.''  His voice was steady, firm.  Bitch spat on the floor and did as he asked, taking the offered crowbar from his hand as they passed each other.  Grue took over the bag filling where Bitch had left off.  We quickly got a rhythm down, and four more bags were filled in a matter of minutes.



``We want to stay to load up the third dog or run for it?'' I asked Grue, then added, ``No use getting greedy.'' I would be happy to leave as soon as possible. I wasn't interested in the money, and I definitely wasn't interested in going to jail for it.



``How much do we have?'' he glanced over in Angelica's direction



Tattletale answered for me, from where she stood at the door to the vault, ``Forty one thousand, eight hundred. It looks like that's as much as we're going to get. The white hats are here, and it's not looking good.''



We were out of the vault in a flash, and we joined Regent at the front doors, peering through the gaps in the wall of darkness.



Tattletale hadn't exaggerated. Our opposition was lined up on the sidewalk across the street, the colors of their costumes bright in the midst of the gloom of the rain and the gray of the city.  Aegis, tan skinned, was wearing a rust red costume with a matching helmet, both with silver-white trim and a shield emblem. The cockroach, I'd come to think of him.  The boy with no weak points.



A dozen or so feet to his right was Vista, wearing a costume with a skirt, all covered in wavy, swooping lines that alternated between white and forest green. She had some body armor worked into her costume design.  Her breastplate was molded to give the illusion of a chest, but that didn't do anything to conceal the fact that she was still young enough that \emph{I} could have kicked her ass in a straight up fistfight.  If she was older than twelve, she was a late bloomer.



Clockblocker stood to Aegis' left. He wore a white costume, skintight, with interlocking panels of glossy white body armor placed wherever they could give him protection without inhibiting his movements. I couldn't see it through the rain, but I knew from TV that the armor had images of clocks on it in dark gray.  Some of the images on the armor were animated so they drifted across the surface, while others were fixed in place with hands ticking. His helmet was faceless, just a smooth expanse of white.



``Tattletale,'' Grue growled in his echoing, reveberating voice, ``You know how I say you're a fucking dumbass sometimes?''



The three weren't alone. Kid Win was floating in the air to one side of Clockblocker. His brown hair was damp in the rain, he had a red visor and body armor in red and gold. His feet were firmly planted on his flying skateboard, which had a ruby glow radiating from the bottom.  His hands were gripping matching guns.  Laser pistols, or something in that vein.  Kid Win was saying something to Gallant, who was standing a ways to his left.  Gallant was an older teenager in a gunmetal and silver costume that blended the appearance of a pulp science fiction hero with a medieval knight.



On the opposite end of the line was someone I didn't know. He was big in a different way than Grue was big. The kind of bulk that made you think powers were at work. His muscle laden arms were bigger around than my thighs, and I thought he could probably crush cans between his pecs. His costume was little more than dark blue or black spandex with a diamond print. His mask was full-face, except for the eyes, and had a crystal attached to the forehead.  He was the only person standing there who didn't have body armor.  He didn't look like he really needed it.



``Who is he?'' I asked, pointing.



``Browbeat,'' Tattletale sighed, ``He's a point blank telekinetic, which means that he can move things with his mind, but only if they're within an inch or so of his skin. He can use it to throw punches that hit like freight trains, or shield himself from incoming attacks. He's also packing personal biokinesis, which means he's got a kind of ability to manipulate his own body. He can heal just by concentrating on an injury, and he's used it to bulk up. He might be capable of doing more on the fly, depending on how much he's trained since we saw him last. He's been a solo hero in Brockton Bay for a little while.''



``What the fuck is he doing here?'' I asked.



``We crossed paths with him once, Regent and Bitch beat him. Either he's here for revenge or he's joined the Wards very, very recently. My power's suggesting it's the latter.''



``That's is the kind of thing you're supposed to inform us on well in advance,'' Grue hissed at her, ``And there's not supposed to be six of them.''



``There's seven,'' Tattletale said, wincing as Grue slammed his fist against the wood of the door. ``There's someone on the roof.  I'm not sure who, but I don't think it's Shadow Stalker. Might be a member of the Protectorate.''



``There's not supposed to be six \emph{or} seven!'' Grue roared in his unearthly voice ``There's supposed to be three, four at most!''



``I made an educated guess,'' Tattletale spoke in a low voice, ``I was wrong.  Sue me.''



``If we get out of this in one piece,'' Grue spoke, his tone low and menacing, ``We're going to have a long conversation.''



I rested my forehead against the window.  An armored section of my mask clinked against the glass, ``Educated guess.  It would have been nice if you had said it was an educated guess, way back when we were planning this.''



Of our group, Bitch seemed the least daunted.  ``I can take them.  Just let me go all out.''



``We're not going to fucking risk killing anyone,'' Grue told her. ``We're not maiming anyone, either. The plan stands.  We have the money, we run for it.''



Tattletale shook her head, ``That's what they want. Why do you think they're lined up like that? We bolt with the money from any of the exits, the person on the roof tackles us, incapacitates us or keeps us busy while the rest close in.  Look at how they're sort of spaced out.  Just far enough apart that if we try to go between them, one of them can probably close in fast enough to nab us before we get away.''



``With my power-'' Grue started.



``They still outnumber us. There's at least five ways they could take one of us down while we're running, even if they were going in blind\ldots and Vista's in the equation. Figure any distance we need to cover is going to be much farther than it looks, and things get ugly. It wouldn't be a problem if there weren't so many of them.''



``Fuck,'' Regent groaned.



``We can't just stay here,'' Grue said, ``Sure, they're getting cold and wet, but our odds aren't much better if we force them to come in here after us, and if we wait too long, the Protectorate might show, too.''



``We have hostages,'' Bitch said, ``If they come in here, we take out one of the hostages.''  Somewhere behind us, someone moaned, long and loud. I think they'd heard her.



I closed my eyes and took a deep breath. It was a bad situation, and worse, I was afraid it was my fault. I'd warned Armsmaster something was going to happen. I could believe that he'd told the teams to be ready to go out in force. Even worse, \emph{he} could be the unknown person on the roof. If that was the case, and Tattletale caught on, I was supremely fucked.



Fuck.



``We need to catch them off guard,'' I didn't realize I was speaking aloud until the words left my mouth.



``Sure, but how are we going to do that?'' Grue replied.



``You guys are masters at the getaway, right?  So we change gears.  We fight them face to face.''





