





I can imagine how it looked to the Wards.  One moment they were standing in the rain, waiting with a tense readiness.  The next, the front doors of the bank slammed open, revealing nothing but total darkness.  Just a moment later, eight hostages came stumbling through the darkness, out the doors and down the stairs.



Aegis' eyes opened wide behind his mask.  He turned to look at Clockblocker, who gestured madly towards the ground.  Turning back to the scene, Aegis bellowed, ``Everyone leaving the bank!  Get down on the ground now!''



He didn't get a chance to see if they listened.  Darkness swelled at the bank's entrance, then flooded into the street like water from a broken dam.  In seconds, the hostages were hidden from sight and the Wards were forced to retreat several paces to keep from being swallowed up.



Inside the bank, Grue mused, ``That should give them a reason to think twice before blindly opening fire where they can't see.  I'm liking this.  We ready for part two?''



``Just don't hurt the hostages,'' I said, glancing back at the thirty that were still inside.



``The ones we sent out are staying put?'' Grue asked.



I felt out with my power.  The bugs I'd put on the hostages couldn't see or hear anything, and I wasn't sensing movement.  ``They're doing as we told them.  They ran as far as they could before your power hit them, and then they lay flat on the ground, hands on their heads.''



``Then I'm going,'' Bitch announced.  She grabbed a bone spike that was jutting out of Judas' shoulder and heaved herself up to a sitting position on his back.



``No,'' Tattletale said, grabbing at Bitch's boot, ``Wait.''



Bitch glared down at her, clearly annoyed.



``That hesitation before Aegis gave the orders to the hostages\ldots it didn't fit.''



``If you've figured something out, spit it out,'' Grue spoke in his echoing voice, ``We need to move now, before they get reorganized!''



``Bitch, you're going after Clockblocker.  Stay away from Aegis, got it?''



Bitch didn't even respond, digging her heels into Judas' sides and ducking her head to avoid hitting it on the top of the door as they raced out.



``What the fuck are you doing?'' Grue growled, ``She's going-''



``They switched costumes.   Aegis is wearing Clockblocker's costume and vice versa.''



I would have liked to see the expression on Brian's face, but as Grue, his mask covered everything.  He just turned his skull-helmet back to the window, silent.



It dawned on me how badly that could have fucked us.  Bitch's dogs would have attacked the person they thought was Aegis, and gotten tagged by Clockblocker instead.  In one fell swoop, we would have lost the majority of our offensive power.



``Good catch,'' I told Tattletale, before raising my hands and directing a good portion of my bugs to drop from the ceiling and flow out the door.



Tattletale only grinned, before she made made her way back to the computer to continue her mad typing.  Grue and Regent headed out the doors, leaving Tattletale and I alone in the bank lobby.



For my part, I walked to the corner of the bank and peered out through one of the tall, narrow windows by the loan officer's desk.  Tendrils of Grue's darkness still clung to the window, but I had a pretty decent view of the battlefield.



As I watched, that view distorted, as if I was looking into a funhouse mirror, or through a drop of water.  The street, including the area with the darkness covering it, began swelling, broadening, and widening until the two sidewalks on either side of the street were more like semicircles than straight lines.  It hurt my head to think too much about how Vista's powers worked.  Or maybe the headache I felt looming had something to do with the fact that I was sending my bugs into the area Vista had distorted.  It wasn't outside the realm of possibility that my brain was having trouble relaying my bug's positions to me as well as it should, in that area where geometry wasn't working quite as it should.



Either way, something was getting to me.  I raised my hands to rub my temples, remembered my mask, and sighed, folding my arms instead.



I sent my bugs through the darkness and the warped space of the street.  Each time they collided with someone inside the cloud of darkness, it took me a moment to figure out who the person was.  Grue was the first I ran into, and the easiest to identify.  Some of my bugs had tiny hairs on their bodies that could sense air currents, and the steady output of darkness around Grue generated something like a steady air current around him.  Regent was harder – I almost mistook him for a hostage – but he was wearing the hard mask over his face.  I left him alone.



I found the person I was looking for, Bitch, and tracked her movement through the darkness.  My bugs could feel the vibrations of the dogs' footfalls on the street, the hot, moist huffs of air from Judas' nostrils, and the smells of the dog.  His smell made a dozen instincts of mosquitoes and carrion flies kick into action, his scent was one of blood, meat and gristle, the vaguest hints of diseased flesh.  I shivered.  As Bitch and her dogs burst from the darkness, towards Aegis and Clockblocker, I had my bugs follow immediately after them.



She was going straight for Clockblocker, who was dressed as Aegis.



``No, no, no,'' I muttered, ``You idiot.''



At the last possible second, she changed course and went for the real Aegis.



Aegis bolted the second the dog changed course, but it was too late.  As he tried to fly out of reach, Judas leaped, nearly twice as far and high as I might have guessed something as big as he was could.  The dog's prehensile tail wrapped around Aegis' torso.  As they all fell, mount, rider and ensnared captive, Bitch shouted something I couldn't hear, and Judas whipped Aegis straight down, adding the force of the throw to the momentum of the fall.



I thought I might have heard the impact from the interior of the bank.  Or maybe it was as auditory illusion and my bugs were the ones who heard it.  Either way, Aegis hit the ground hard enough to kill an ordinary person.



He wasn't down for one second before he was on his feet again.  In the same motion he used to get to his feet, he lunged for the dog and swung a fist at Judas' snout.  He might have connected, but Bitch was already steering her steed back into the cloud of darkness.  She flipped Aegis the middle finger before disappearing from view.



At the same time, Clockblocker was fighting off the bugs I'd sent out.    Within a fraction of a second of a bug making contact with Clockblocker or his costume, he froze it.  My power simply stopped telling me the bug was there, as if they had disappeared from the face of the planet.  In reality, they were just suspended in time.  Stuck in the air, immobile, untouchable.



But that same power could work against him, I was thinking.  I made my bugs surge forward, surround him, aiming to cover his entire body.  I was pretty sure he couldn't disable the effects of his power, so if he wanted to freeze all of the bugs I had crawling on him, he'd trap himself in a prison of his own making.



He was good at thinking on his feet, though, or he'd faced similar tactics before, because he had an answer for that.  Clockblocker spun in a tight circle, freezing the bugs as his body rotated, so that they were only affected when the part of his body they were on was facing away from the bank.  The result was that a cluster of bugs was left frozen behind him, and he was free to dash straight towards Aegis.



While I'd been distracted by Clockblocker, Bitch had set Brutus and Angelica on Aegis.  He was fending the two dogs off, but the white pane of his helm – Clockblocker's helm – was shattered, now, and his costume was torn with one piece of ruined armor dangling by a string of cloth at his armpit.



Brutus lunged for Aegis, but as he passed over the edge of the area Vista had distorted, he fell short.  The dog's jaws clacked shut a foot away from Aegis' face, spittle flying.



Aegis responded by slamming both fists, fingers interlaced, into Brutus' snout.  The dog crashed onto its side, giving Aegis the time to take flight once more, heading straight for the sky.



Angelica followed, leaping through the air just like Judas had a minute earlier.  She missed, and hit the side of a building hard enough to make the windows around her explode in a spray of glass.  I waited for her to fall, but she apparently had no plans to do so.  She gripped the stone of the building and windowsills around her with her four claws, tensed, and leaped again from the side of the building.



If I was surprised to see that display of acrobatics from one of the dogs, I doubted there were words for what Aegis' must have felt, just then.  Angelica seized the teen hero in her jaws and they plummeted together.



Angelica didn't land with all four claws beneath her, and she sprawled as she hit the ground.  When she stopped, though, she still had Aegis, one of his arms and half his torso clasped between her teeth.  She whipped him around like a dog might shake a toy.  When she paused, he was still fighting her, slamming his free hand against the side of her head over and over.  Loops and strings of drool mixed with blood hung from her mouth.  At least, that's what I thought it was, from my vantage point inside the bank, peering through gloom and pouring rain.



Clockblocker had slowed down as I started throwing more bugs in his way.  I kept them between him and Aegis, so he couldn't close the distance and touch the dogs.  He'd responded by ducking, weaving, spinning and swatting or brushing them off with his hands, so he could freeze them without setting barriers in his own way.



Then he decided to try ignoring the swarm.  I seized the opportunity to bite and sting him twenty or so times.  The surprise and pain distracted him from his evasive maneuvers, and he wound up clotheslining himself as he froze the insects on his face while still running forward.  He went from a head on run to landing on his back with his feet still in the air.



I probably wouldn't get a better chance.  I set the majority of the swarm on him while he was lying on the ground.



Keep them on the defensive, Brian had told me, while we sparred.  Keep them guessing, change the way you attack.



I directed the bugs to the areas where his skin was exposed, and piloted them into the gaps between his skin and his costume.



Even with innumerable insects biting and stinging him over and over, he managed to climb to his feet and return to his attempts to reach the dogs.  He knew as well as I did that he couldn't freeze them now that the bugs had made their way inside his costume.  He'd have to rip his costume with his own strength if he did.  I doubted it was that easy to tear, either.



It was ironic.  I wouldn't have been able to do this if he hadn't switched costumes with his teammate.  Clockblocker's usual costume covered every inch of his skin, like mine did.  Probably for much the same reason.



``I'm so sorry,'' I murmured, just loud enough that only I could hear it.  I gave the bugs a new order.



When the bugs started crawling up his nostrils with relentless intent, he managed to keep going, pulling himself to his feet and resuming his efforts to freeze the bugs while advancing towards the dogs.  He snorted to try and clear his nose so he could keep breathing, but then he was left with the problem of needing to inhale.  He couldn't do that without bringing bugs further into his airway, so he made the mistake of opening his mouth to breathe.



When a mass of bugs forced themselves into his open mouth, he staggered and fell.  I think he was gagging, but couldn't see or hear well enough from my vantage point to tell.



At my instruction, more bugs forced themselves under the gaps in his costume and into his ear canals.  Yet others, smaller ones, crawled in and around his eyes, using deceptive strength to try and force themselves in between and under his eyelids.  I couldn't imagine what that felt like to him.  Everyone had probably experienced the sensation of having a lot of bugs crawling on them, but these bugs were operating with a human intelligence backing them, to penetrate his eyes, ears, nose and mouth.  They were working together, with a single minded purpose, instead of mindlessly crawling where their instincts directed them.



I don't know if it was calculated or something he did in a moment's panic, but he used his power.  Every bug that was touching him disappeared from my reach.



Once I'd realized what he'd done, I pulled away every bug that wasn't affected.  I didn't want to suffocate him, and he'd effectively pinned himself to the street with his power.  The worst thing that could happen now was that he'd panic and throw up, choking on his own puke.  I could do my part to avoid that.



I'd won.  I wasn't sure what to feel.  I felt a kind of elation mixed with the quiet horror of what I'd just done to a superhero.



I could settle that inner turmoil later and decide on a way to make amends to Clockblocker at the same time.  There were still five Wards and a stranger on the rooftop to be taken out, if I wanted to stay out of jail.

















