





Six good guys were still in action, as far as I knew.  Clockblocker was down, and posed no threat unless someone walked into his reach where he was lying down, or unless we took longer than the ten or so minutes it would take his power to release him.  Angelica and Brutus were playing a macabre game of tug of war, using Aegis as the rope.



The rest of the battlefield was chaos.  Patches of darkness covered everything, and the landscape was distorted.  In some of the areas Vista had warped, the rain wasn't falling in a straight line.  One spot in particular had the rain moving horizontally before it dropped to help fill a massive puddle thirty feet across, where her power had made an indent in the ground.



Aegis and Clockblocker were more or less dealt with.  As Vista was the last remaining priority target,  I directed my remaining swarm towards her.  They wouldn't reach her quickly though, as the rain bogged them down, and both puddles and distorted space forced a more roundabout route for the bugs.



Bitch, still riding Judas, came rushing out of a cloud of darkness, splashing through the huge puddle.  Kid Win and Gallant opened fire on her with laser beams and painfully bright blasts of energy.  She was moving fast and unpredictably enough that Judas only took one or two glancing hits.  The distance between her and Vista rapidly closed.



Vista raised her hand, and the surface of the street bulged upward into a short wall.  As it grew, the wall caught one of Judas' forepaws, tripping him.  He fell, and his rider was sent tumbling head over heels.



Bitch got to her feet before Judas did, but only managed to take a single step before one of Gallant's blasts clipped her.  I winced.  His light blasts were charged with energy that made the people struck feel a particular emotion.  Gallant could blast you with one that made you hopeless, scared, sad, ashamed\ldots



Bitch screamed, and it was a long and primal noise, filled with rage.  I was still inside the bank, watching things unfold through the window, barely able to hear it, and it still made my skin crawl.  So he'd shot the dangerous psychopath with a blast that made her \emph{angry.  }Someone would have to explain that one to me at a later date.



Whirling, still screaming, she pointed at Gallant.  Apparently that was order enough, because Judas charged at the teenager that was dressed like a science fiction Lancelot.



Bitch didn't attack him though.  Without her dogs at her back, essentially without powers, she went straight for Vista.  She was focused enough to stay on the priority target.



Vista was ready, though.  As Bitch tried to close the distance, the roadway between her and the young heroine stretched out, until the distance she had to cover was two, three, four, five times as far.  Vista then pinched the space behind her closer together, crossed a third of a block with a single skip, and then returned it to normal.  I swore under my breath, and not just because my bugs had a lot more distance to travel.  My head was pounding again, and it was getting steadily worse.



Was someone's power at work, giving me a headache?  There wasn't anyone in the Wards, I was pretty sure, who could mess with your head like that.  Gallant could mess with your emotions, but he had to hit you with a light blast to do it.  The person on the roof, then?  I was fairly confident there wasn't anyone in the Protectorate or New Wave who could affect me like this.



Bitch gave up on Vista and whistled for Judas.  The dog responded immediately, abandoning his skirmish with Gallant, who was trying and failing to stand.  A wash of darkness consumed him before he managed to pick himself up.



Kid Win opened fire on Bitch as her dog returned to her.  Given the excessive distance between them – it would have been a hard shot to make \emph{before }Vista stretched the area that Bitch was standing on – meaning his aim was wildly off target.  He stopped, changed a setting, and fired a fresh salvo.  This time, the lasers came out in more of a staccato spray, like you'd expect from a machine gun.  One of the lasers caught Bitch in the center of her stomach and laid her flat.  Judas guarded his owner by hunkering over her, blocking further shots and obscuring my view of her.



Near Vista, a large figure staggered out of the darkness, shadows still clinging to him, bellowing and screaming incoherently about bugs.  He thrashed for several moments, then collapsed into a heap a short distance from Vista.  Someone that large could only be Browbeat.  Vista apparently reached the same conclusion I did, because she took a few steps closer to him, looking around helplessly for a way to help him.



An instant after I realized that I didn't actually have bugs on Browbeat, the figure struck Vista across the side of the head, laying her flat.  I saw the briefest glimpse of Grue's skull mask before he and Vista were covered by a fresh tide of his darkness.



``Bitch, Vista, Clockblocker, Gallant are out of action, I think,'' I called across the room to Tattletale, who was still hammering away at a keyboard.  ``We've got Aegis handled for the time being.  Not sure what happened to Browbeat, but there's only him, Kid Win and the person on the roof to deal with, now.  We can make a break for it soon.''



``One last thing to do,'' Tattletale grinned to me, ``I'll be right back.  Keep an eye on things here.''



``What?  No – Tattletale!  Dammit!'' I shouted, but she was already running, heading back into the offices that we'd been through on our way to the bank.



I didn't have time to dwell on her leaving.  Flickers of light outside the bank caught my attention.  Kid Win was flying fifteen feet above the ground on his hoverboard.  In front of him, pieces of a massive device were materializing, shimmering into existence like you saw with the transporters on Star Trek.  It was only one or two steps away from being complete, but you could tell what it was.  A gun, no less than fifteen feet long, with a barrel three or four feet across, all turret mounted on a circular platform not unlike the board he was riding.



``Shit,'' I whispered to myself.  I sent my bugs after him.



He swiveled the cannon to face Judas, who was still guarding the spot where Bitch had fallen.  A bolt of light erupted from the cannon and sent Judas flying beyond my field of vision.  He fired another shot, at a greater distance, presumably at the fallen dog.  Then he swiveled and fired off two more shots in quick succession, blasting Aegis and the two dogs that were gripping him.



The dogs and Aegis were all sent flying into the wall of the office building opposite the bank.  While the dogs didn't get up immediately, a bloody and tattered Aegis was on his feet in an instant, and in the air a moment later.  He got to a good height – maybe two or three stories up, and stayed there, likely to get his bearings and survey the situation.



As my bugs approached the Kid, he took notice and maneuvered his cannon to decimate the swarm.  I spread them out, but he simply pulled a lever and released a flamethrower-like blast of lightning and sparks, eliminating virtually all of the bugs I'd sent out into the street.  The scant few that that remained, I sent towards his face, to crawl beneath his visor and into his nose and mouth.  It wasn't enough.



Then Kid Win aimed the cannon straight at me.



I jumped for cover the moment I realized what he was doing.  There was a muffled sound, more a very large person someone hitting a punching bag than what I'd expect a laser cannon to sound like, and the window exploded.



What was he doing?  We had hostages inside.  I turned to check, and saw there weren't any hostages near me.  Did he know that?  Heat sensors in his visor?  Was someone watching me through the cameras and passing him info?  Damn it!  There was too much I didn't know, and Tattletale wasn't around to fill me in.



Grue sprinted between two clouds of darkness, raising one hand to send a blast of his power towards Kid Win, obscuring the Kid's line of sight.  Kid Win responded by ponderously maneuvering himself and the cannon out of the top of the cloud of darkness.



I swore under my breath and sent a command for more of the bugs I had inside to drop from the ceiling and go outside to attack.  There were a good few bugs near Clockblocker, who were getting free of the time stopping effect he'd laid on them.  I added those to the assault.



My legs buckled as my headache worsened tenfold.  Worse, the response from my bugs was sluggish, like I was ordering them to move through mud.  I felt a momentary panic, but there wasn't really anything I could do.  I grit my teeth and ordered the attack anyways, then forced myself to run for the other side of the bank, in case he could somehow detect me and shoot through the walls to hit me.



I glanced through the windows for Aegis as I passed them.  Through the rain, and the darkness that lingered on the surface of the windows, I spotted him.  His white costume was wet with rain and ridiculous amounts of blood, and he was diving straight for the bank like a human missile.  Damn it.



Inexplicably, his descent wavered, then curved.  He flew straight into the ground, full force, hard enough to crack pavement.  One of the dogs, I couldn't tell which, had managed to extricate itself from the rubble of the shattered wall and rushed at the fallen Aegis.



Kid Win was occupied trying to do three things at once – he was maneuvering out of the way of the clouds of darkness Grue was setting in his way, making return potshots at Grue as Grue zig zagged between spots of cover and with every free moment, he was blasting hundreds of my bugs out of the air.  If my power was at full strength, my bugs probably would have reached him already, but something was interfering.  That, or I'd overexerted myself.  The bugs were slow to react, slow to move and some were slipping from my grasp, returning to their instinctive behavior.  Making matters worse, I wasn't blind to the fact that every time I gave a command, my headache got exponentially worse.



With Kid Win occupied as he was, the dog had a clear path to Aegis.  Aegis didn't try to run this time.  He stood his ground and reached for his utility belt.  He retrieved something that looked like a miniature fire extinguisher.



Then he pulled the pin.



For the second time in a matter of minutes, I dove away from the window.  It wouldn't be a grenade, but the option that made the most sense-  I squeezed my eyes shut and covered my ears just in time.  The explosion the flashbang grenade made was enough to leave me breathless, and there was a stone wall and some fifty or so feet between us.



I chanced a careful look through the window as soon as I'd recovered, hands still over my ears.  The dog was reeling, making pained sounds, and Aegis was pummeling it, using his flight to close the distance and add more momentum to his swings.  When the dog, Angelica, I saw, looked like it was starting to recover, he grabbed two more flashbang grenades from his belt with one hand and pulled the pins with the other, dropping them to the ground just below him.



I ducked behind cover again, but they didn't go off.  When I chanced another look, I saw the tables had turned.  Where the flashbangs had been dropped, there was a smudge of Grue's darkness covering the ground.  Angelica was having it out with Aegis, and Regent was striding out of the darkness, in Kid Win's direction.



I'd forgotten about Regent.  It made sense that he was working from a discreet position like I was.  He probably would have been the one to alter Aegis' flight path.



Seeing Regent approach, Kid Win turned his turret-mounted cannon in his direction.  Before he could fire, though, Regent raised two fingers, and Kid Win lost his footing on his flying skateboard.  The cannon shifted until it was pointing straight up, as the young hero dangled from the handles, his weight altering the trajectory of the cannon.  His board clattered to the ground a few feet away.



Regent made a dismissive wave, and Kid Win let go with one hand, his fingers and arm curling backwards in a palsied fit.  Regent repeated the gesture, and Kid Win lost his grip on the controls, dropping a good twenty feet to the asphalt.



As Regent approached to stand over him, Kid Win reached for his laser pistol.  He scowled in frustration as his fingers continued to twitch and curl involuntarily, instead of closing on the handle of the gun.



With an almost relaxed air, Regent shoved the end of his tazer into Kid Win's side.



I don't know if it was the sense of relief, but I couldn't help but laugh as Regent collected the fallen skateboard and began a wobbly ascent to the floating cannon turret.  He aimed and began firing at Aegis, who was forced to scramble out of the way.



``What's so funny, psycho?''



I whirled to face the voice, and saw the freckled, brown haired hostage that had been glaring at me when we'd first taken control of the bank lobby.  After that, I saw only stars as she slammed something large and blunt into the side of my head.

















