





I crashed into the office chair behind me and both the chair and I toppled to the ground.  The armor of my mask had taken the worst of the hit, but it still hurt as much as anything I'd ever experienced.



The girl glowered at me from behind her mop of frizzy brown hair.  In her hands she was gripping a fire extinguisher.  Behind her, past the lights that were flickering across my field of vision, I could see the hostages streaming upstairs.  It was disorienting, because the bugs I'd left on them were telling me they were still in the corner of the lobby, staying still.  I could feel one spider shift slightly as the person it was riding exhaled, then shuddered a little, even as I saw that same person stumbling and nearly falling on the stairs in their haste to get away.



I reached for the bugs, tried to tell one to move, and everything went wrong.  There were no words the words to describe it, exactly.  It was like feedback.  If my brain had been a computer, I got the feeling I'd only be getting hundreds or thousands of error messages popping up across the screen.  It was painful, too, just compounding until it felt like my brain was being used as a punching bag.



I pressed my hand to my head, wincing at the pain, and it wasn't just from being bludgeoned with a fire extinguisher.  The headache was at near-migraine levels now, and I desperately wanted to tear off my mask and try to throw up, if only to relieve of the nausea that was welling up.  I was getting an idea of why I'd been feeling so off.



``What the fuck did you do?'' I asked the girl.



``You don't need to know that.''  She swung the fire extinguisher over her head at me, and I scrambled out of the way, grabbing the edge of a table to haul myself to my feet as I did it.



She didn't chase me.  Instead, she reached into her jacket pocket and retrieved a cell phone.  She started to punch a number into the keypad with one hand, the other holding the fire extinguisher.  Her eyes were trained on me.



There was no way I was going to let her make that phone call, whoever she was dialing.  I went on the offense, lunging towards her as I reached into the armored compartment at my back and retrieved the extendable baton.  I pulled the trigger and flicked it out to one side.  Eighteen inches of black painted alloy with a weighted tip snapped out from the foam-grip handle.



Her eyes widened as I swung the baton, but she had the presence of mind to drop the phone and heft the fire extinguisher up to block the attack.  Her grip on the fire extinguisher wasn't good enough for her to keep hold of it, so it clattered to the ground.  She backed away rather than risk trying to pick it up again.



The girl retreated as I advanced towards her.  I stopped when I was standing over her cell phone.  I collapsed and sheathed my baton, then bent down and retrieved the fire extinguisher.  I smashed the phone with the butt end of it.



``Shit.  I liked that phone,'' she muttered.



``Shut up,'' I retorted, the pain making my voice strained, harder edged, ``What the fuck did you do to me?''  I pressed the heel of my free hand against my forehead, as if the pressure could help stave off the pain.



``I\ldots don't think I'll tell you.''



``Who the fuck are you, and who were you trying to call?''



``Actually, it was a text, not a call, and it went through,'' she said.  Then she smiled at me.



At the same moment I uttered the word `Who', one of the windows at the side of the bank shattered.  A blur of white and gold slammed into the center of the lobby hard enough to send fragments of marble tile skittering over the floor to my feet, halfway across the room.



The figure straightened, dusted herself off and turned to glare at me.  Almost casually, she backhanded the marble and oak table to her left that held all of the withdrawal and deposit slips.  With that lazy swing of her arm, she annihilated the table, doing so much damage to it that nobody would ever be putting it together again.



It's humiliating to admit, but I nearly wet myself.  I'm not sure my reaction would have been much different if she didn't have a power that made her flat out terrifying.  Literally, that's what her power did.  Had I done something heinous in a past life, to deserve going up against Lung on my first time out in costume, and Glory Girl on my second?



``Hey sis,'' Glory Girl tilted her head to one side, to look at the brown haired girl, ``You okay?''



The girl, who could be none other than Amy Dallon, Panacea when she was in costume, offered Glory Girl a beaming smile, ``I am now.''



Glory Girl's sister had been among the hostages.  Damn it.  At least I knew who she was now.  She could heal with a touch, and if what she'd done to my powers was any indication, that wasn't the full extent of her abilities.  Glory Girl and Panacea were celebrities, even if Panacea had generally avoided the spotlight as of late.  They were among the most famous of the local heroes, arguably among the most powerful of the kid capes, they were pissed at me, and I was stuck in a room with them.



And my powers weren't working.



Glory Girl stepped towards me, and I scrambled for Panacea.  She scrabbled for a grip at my costume, trying to grab at my glove, then at my mask,  but the moment I drew my knife, both she and Glory Girl went absolutely still.  I grabbed Panacea's chin and maneuvered so I was standing behind her, my knife pressed to her throat.



``Count yourself lucky, bug bitch, that your costume covers your entire body,'' Panacea murmured to me, ``Or I'd maybe give you a heart attack.  Or cancer.''



I swallowed hard.  I wasn't counting myself as particularly lucky at this point.



``It seems we have a stalemate,'' Glory Girl said.



``True,'' I replied.



``So are we just going to stand around here until reinforcements arrive for one side or the other, tip the scales in someone's favor?''



``I could live with that.  Last I saw, my side was winning.''



``I helped Aegis out of a jam on my way in, so he's keeping your little friends busy.  You should also know that the Protectorate is on their way from a wine and dine with Brockton Bay's finest at the Augustus Country Club.  Can't speak for them, but I know I'd be royally pissed if some little snots dragged me away from a chance to have the club's chocolate mousse.''



Panacea made a little laugh, ``It is good, isn't it?'' then in a lower voice, she whispered to me, ``What if I fucked up your taste buds, you little terrorist?  You threaten the lives of innocents, I can go that far.  I can do anything with your biology.  Make everything you eat taste like bile.  Or maybe I'll just make you fat.  Morbidly, disgustingly fat.''



``You can shut up now,'' I tightened my grip and pressed the knife a fraction harder against her throat.  Between the stress of the moment, the pounding headache and the fact that fucking Glory Girl was standing not fifty feet away, I didn't need little sister distracting me with nightmarish imagery.



Glory Girl spoke up, ``It's not just the Protectorate, either.  You just took a member of New Wave hostage, threatened her life.  There's a pretty damn good chance my mom, dad, aunt, uncle and cousins will be showing up, too.  Brandish, Flashbang, Lady Photon, Manpower, Laserdream, Shielder\ldots how are you going to manage, then?''



Fuck.  I had no reply to that.  I kept my mouth shut.  I was barely able to focus, now, as my head throbbed.  My vision was wavering around the edges, and my grip on my bugs was virtually gone.  Most had freed themselves from my influence entirely, and were buzzing around the light fixtures or crawling for darkness.  It was all I could do to stay standing and keep my hands steady.



``Drop the knife and surrender, and I'll make sure you get leniency.''



``I've read up on the law enough that I know you don't have the power to make any deals,'' I said, ``No go.''



``Okay.  Then I guess we wait.''



A few long moments passed.



Glory Girl turned her attention to her sister, ``I wanted to go to the mall for lunch, but noooo,'' Glory Girl said, ``You needed to go to the bank.''



``It was either going to the bank or wind up broke for that double date you're forcing me into.''



``Ames, the guy I'm setting you up with is a sixteen year old millionaire.  I don't think it's unreasonable to expect him to foot the bill for dinner and a movie.''



``Could you two please shut up?'' I growled.



``Do they have to?  It's all very informative,'' Tattletale joked as she sidled into the room.  She hoisted herself up to the edge of one of the teller's stations, then greeted Glory Girl, ``Hey Glory Hole.''



Glory Girl's face twitched.



``Hey, Tattletale,'' I called out, my voice a touch strained, ``Not that I'm not glad to see you, but could you avoid antagonizing Alexandria Junior?''



``Eh.  You seem to have things under control.  Why not set the bugs on the prom queen?''



``Prom queen?'' Glory Girl asked.



``Um,'' I cut in, before either of them could say something that started a fight, ``First of all, she's invincible.  Second, again, bad idea to irritate someone who can swing a schoolbus like a baseball bat.  Third, my hostage here did something to fuck up my powers.''



``That last bit sucks,'' Tattletale sympathized.  Then she took a closer look at Panacea, ``Shit.  Amy Dallon?  Grue is going to kill me, for missing that.  You look different than you did when you were showing up in the news.  Are you wearing your hair differently?''



``Tattletale,'' I interjected, again, ``Less small talk, more problem solving.  Glory Girl said the Protectorate and maybe New Wave are en route.''



Tattletale glanced at Glory Girl, then frowned, ``She's not lying.  Let's start with problem three, since you're not looking so hot.  Your powers aren't working?''



``Can't control my bugs, got a major headache.''



``Think I know why.  Let me fix that for you,'' Tattletale said.  She hopped down from the teller's station and started to walk towards me and Panacea.



``Don't move,'' Glory Girl warned.



``Or what?'' Tattletale whirled to face the girl, smiling, ``You'll beat me up?  You can't do anything while my teammate has a knife to your sister's throat.  Sit.  Stay.  Good girl.''



Glory Girl glowered at Tattletale, but she didn't move.



``I think it would be better if you stayed back,'' I warned her, ``You get in Panacea's reach, she'll touch you and give you a stroke or something.''



``Can she?  Sure.  Will she?  Definitely not.  She's all bark, no bite.''



``Try me,'' Panacea taunted.  I reasserted my grip and reminded her of the knife against her throat.



``I'd really prefer to avoid tempting fate,'' I said, carefully.



``Fine, fine,'' Tattletale said, raising her hands in a placating gesture.  She walked over to the branch manager's desk and opened a drawer.



``You pull a gun out of that drawer,'' Glory Girl threatened, ``And I'll fucking break you.''



``Enough with the threats you can't follow up on.  It's not a gun,'' Tattletale grinned, raising her hands again.  A keychain dangled from her left thumb.



``Keys,'' Glory Girl said.



``The keys of manager Jeffry Clayton.  Type A personality, totally.  Control freak.  The kind of guy who loves to have absolute control over a meeting.''



``First of all, who cares?  Second, how do you know this?''



``Come on,'' Tattletale smiled, folding her arms, ``Villain 101.  You don't give info to the hero in a gloating monologue.''



``Right,'' Glory Girl agreed, ``Always worth a try.''



``I'll tell you anyways.''



Glory Girl raised an eyebrow.



``No reason not to.  Actually in my advantage to let you know.  I'm psychic.  I read his mind when we had him hostage, like I'm reading yours right now,'' the lie was so smooth \emph{I} almost believed it.



A flash of red caught my attention.  The red dot from a laser pointer settled on the hood of Panacea's jacket. I looked at Tattletale, and saw that while she had her arms folded, she was holding a laser pointer that was attached to the keychain.  I watched Tattletale draw a lazy circle around the spot she'd pointed to, on Panacea's jacket.



``Bullshit,'' Glory Girl said, ``The brainpower you'd need to interpret and decode someone's unique neural patterns would need a head five times the usual size to contain it all.  True psychics can't exist.''



``Ooh, someone's taking Parahumans 101 at the university.  Your parents pull some strings, got you into a university course before you were done high school?''



``I think you already know the answer, I'm just not buying that you read my mind to get it.''



``Why is it so hard to believe?  Legend can shoot lasers from his hands, lasers that \emph{turn corners}.  Clockblocker and Vista can mess with the fundamental forces of space and time.  Kaiser can create metal from thin air.  Conservation of mass, conservation of energy, basic laws of our universe get broken by capes all the time.  All of that is possible, but I can't peek into your brain?''



Tattletale was still focusing the laser pointer on Panacea's hood.  Since I was the only person in a position to see it, it could only be for my benefit.  I pulled the hood back, investigated the interior and found nothing.  But on the nape of her neck, I spotted one of my black widow spiders.



I pulled it off her gently, and felt the pain in my head worsen with the contact, the movement.  Either by impulse or by reflex as I flinched at the pain, I crushed it between my fingers.



Immediately, the pain in my head dropped to a fraction of what it had been.  The relief was so intense it was almost euphoric.  I still didn't fully grasp what Panacea done, but I was getting a good picture of it.  She'd somehow sensed what I was doing to control the spider, then altered things so the spider wasn't sending me the right information.  A continuous loop of the wrong information, like when thieves in the movies spliced a video camera feed to repeat the same segment over and over.  Either by accident or design, it had exponentially increased the interference every time my power reached for the arachnids in question.  All building up to a metaphorical short circuit of my power.



I could barely fathom the subtleties and delicacy that would have required to set up.



``Glory Gi-'' Panacea began to speak, but I tightened my grip, and she closed her mouth.



``Shhhh,'' I hissed at her.



``Scholars say you're wrong.''



Tattletale grinned, ``Scholars \emph{want} me to be wrong, and their research reflects that.  Telepathy scares the everloving crap out of people, especially since the only suspected telepath out there is-''



``The Simurgh,'' Glory Girl finished for her.



``Right.  And when a fucking Endbringer is your precedent, people get spooked, just like you're spooked right now, at the idea that there's someone standing in front of you who can find your deepest darkest secrets and tell the world.''



Tattletale was pointing to Panacea's upper arm now.  It took me two tries to murder the spider.  Before I'd finished, Tattletale was directing me to the final one, which I'd stashed on Panacea's ankle. I killed it by jabbing at it with my toe.  The headache was completely gone a second later.



``Which is why you call yourself Tattletale, I see,'' Glory Girl was saying, ``But you're a retard.  We're part of New Wave.  We have no secrets.  That's the whole fucking point of our team.  Heroes with no secret identities, no secrets, full disclosure, total accountability.''



``For the record,'' Tattletale said, her voice very smooth and calm, ``I fucking hate it when people call me stupid.''



``Yet here the two of you are, and neither of you have powers that work against either of us.  All you've got is a knife, and if you use it, you both die in the most painful way I think I can get away with.''



``Oh honey, now who's being stupid?  I've got the most powerful weapon of all,\emph{``} Tattletale purred, smiling wickedly, ``Information.''

















