





``Information,'' Glory Girl repeated.



Tattletale twirled the keys around one of her fingers, ``For instance, it's not exactly public knowledge that Panacea was adopted.''



``It's not a secret either.  It's on official record.''



``Falsified records,'' Tattletale grinned.



Glory Girl glanced at her sister.



``Let me tell you a little story.  Correct me if I'm wrong on any of the details.  Eleven years ago, just five years after capes really started showing up, there was a team operating hereabouts, calling themselves the Brockton Bay Brigade.  Lady Photon, Manpower, Brandish, Flashbang, Fleur and Lightstar.  They wind up taking on a villain in his own home and it's a pretty decent fight.  They beat him, and because he was a real bastard, he got sent straight to the Birdcage.''



``You can stop now,'' Glory Girl said, ``Point made.''



``Oh, I haven't even gotten to the good part.  See, they found a little girl hiding in the closet.  \emph{His} little girl, a toddler,'' Tattletale grinned at Panacea, ``Given the odds that someone with powers would have a kid with powers, and knowing how the little girl would never be able to have a normal life with word inevitably getting out about her past, they wound up taking her in.''



``We know this story already,'' Glory Girl replied, her tone just a touch testy.



Whatever Tattletale was doing, I sensed it was giving us more control over the situation.  I commented, ``This is new to \emph{me}.  I'm sort of intrigued.''



``The point I'm getting at, Glory Hole, is that I know that one detail you two don't.  Or at least, I'm willing to look at all the little clues that you've got floating around your heads and figure out that one thing that you've gone out of your way to avoid knowing.  Glory Hole's curious, but she avoids the subject because her sister desperately wants her to, and Panacea\ldots  Well, if I told her, I suspect she'd do something very stupid.''



I could feel Panacea slump in my arms.  The fight had gone out of her.



``So, Amy, you want to know who your daddy is?''



For a few long moments, there was only the sound of rain pattering on the windowsill, and the buzzing of the insects still in the room.



``It's that bad?'' I asked in a half whisper, as much to Panacea as to Tattletale.



``It's not the man that would bother her so much.  It's the knowing.  Every hour of every day after hearing me say his name, she would wonder.  She's terrified she'll start second guessing every part of herself, wondering if she inherited it from \emph{him}, or if she was that way out of an unconscious desire to \emph{not} be him.  Knowing as much as she does already keeps her awake some nights, but knowing his name, knowing who he is and what he did?  For the rest of her life, she would compare herself to him.  Isn't that right, Amy?''



``Shut up.  Just\ldots shut up,'' Panacea retorted, her voice thick with emotion.



``Why?  I'm on a roll.  That's not even the most dangerous tidbit of info I've picked up, here.  I know stuff that's just as bad.''



I saw a flicker of doubt cross Glory Girl's face.



``I'll make you a deal, Glory Hole.  You go in the vault, lock yourself in, and I don't speak on the subject.  I won't say the one sentence that tears your family apart.''



Glory Girl clenched her fists, ``I can't do that.  I'm calling your bluff, and if I'm wrong, I'll face the consequences of whatever you say.''



``Very principled.  Very self-involved too, that you think the secret and the consequences have to do with you and your overzealous nature.  They don't.  They have to do with \emph{her.}''  Tattletale directed the laser pointer at Panacea's forehead, ``You won't be tickled pink, either, but the aftermath would be hers to deal with.  Humiliation, shame, heartbreak.''



I could feel Panacea stiffen in my grip.



``Offer stands,'' Tattletale grinned, ``For the next twelve seconds.  Get in the vault.''



``You're full of shit,'' Panacea spat the words.



``Then why are you so tense?'' I asked.



``Eight seconds.''



Panacea abruptly tore out of my grip, so violently I had to pull the knife away to keep her from cutting her own throat against it.



Tattletale scrambled to put a desk between herself and Panacea, but Glory Girl slammed into her, carrying her across the length of the room.  They stopped just short of a wall.  Not that Tattletale got away unscathed.  Glory Girl shoved Tattletale into the wall, one hand over her mouth, and held her there.



While Panacea was distracted, I passed my knife into my left hand and gripped my baton.  I pressed the trigger while swinging it, letting the momentum of the swing draw it out to its full length.  Panacea saw me coming, but I don't know if she realized what I was holding.  The length of metal struck her across the side of the head.  She staggered a few feet, then went down hard.



Unfortunately for me, Glory Girl saw it all unfold.



``Nobody fucks with my family!'' she shouted, and her power cranked out full-bore.  My knees turned to jelly and my brain just gave up on rational thought.  Glory Girl threw Tattletale at me like a very strong child might throw a rag doll, and I just stood there like a deer in the headlights.



Tattletale's body collided with my midsection, knocking the wind out of me.  The two of us collided with a desk, sending a monitor and a plastic box of files to the floor.  Paper and fragments of monitor scattered over the ground.



We were still reeling when Glory Girl started floating towards us.  I was struggling, unsuccessfully, to heave wheezing gasps of air into my lungs, while Tattletale was gripping one of her arms tight against her body, making little whimpering noises.



``I'm going to pull in every favor I'm owed, and put myself in debt with the local D.A. and whoever else I have to, to get you both sent to the Birdcage,'' Glory Girl promised, ``You know what that place is like?  A prison without wardens.  No communication with the outside world.  No escapes yet, which is pretty amazing considering it houses all of the worst and most powerful villains we've been able to capture.  We don't even know for sure if anyone's alive inside there.  It's just a bucket where we dump scum like you, so we never have to worry about you again.''



``Bugs,'' Tattletale grunted at me, almost too quiet to hear.



I didn't catch her meaning, but I was still struggling to catch my breath, so I just shook my head at her.



``And no contact with the outside world means you don't go fucking talking about whatever Amy wants to keep private.  I trust my sister, I trust she has a reason for keeping it to herself.''



``Bugs.  Swarm her,'' Tattletale said, taking lots of little breaths as she said it.



I caught her meaning.  I reached for my swarm, and was glad to find that my power was working perfectly.  Panacea's sabotage job had been undone when I'd killed the last of the spiders.  I set every bug I could reach on Glory Girl.



Useless.  It felt like I'd set them on unnaturally strong, slick glass.



``Idiots,'' Glory Girl's muffled voice came from the midst of the cloud of insects, ``I'm invincible.''



Tattletale used her good arm to prop herself up, groaning, ``First of all, I warned you about calling me stupid.  Second, no, you're not invincible.  Not exactly.''



Then she raised her good hand from her belt and trained a small handgun on Glory Girl.



The sound was deafening.  You don't really get a sense for how intense gunfire is from TV and movies.  As is, it was enough that it took me a few seconds to get a grip.  Just a heartbeat later, I realized my bugs had broken through.  They found flesh to latch on to, flesh to bite, sting, claw and puncture.  Glory Girl dropped like a stone and started thrashing violently.



``Help me stand,'' Tattletale's voice was strained, ``Using my power like that on them took a lot out of me.''



I grabbed her good hand and helped her up.  With one of her arms around my shoulders, we hurried out of the bank, together.  She shoved the gun into one of the largest pouches of her belt.



``What--'' I tried, but talking just sent me into a spasm of painful coughs.  We were down the front steps of the bank before I felt like trying again, ``What just happened?''



``She's not really invincible.  That's just an idea she likes to put in people's heads.  She has a forcefield around her entire body, but it shorts out whenever she takes a good hit, comes back online a few seconds later.  I knew when I saw she had dust on her costume.  Dust that her forcefield would keep off her.  Fuck, this hurts.''



``What is it?''



``She pulled my arm out of the socket when she threw me.  Can you fix a dislocated shoulder?''



I shook my head.  I knew how, generally speaking, from the first aid classes I had taken, but I doubted I had the strength to manage it, and I didn't want to waste time getting Tattletale in a good position to fix her arm when we needed to be gone.



The fight outside the bank was still going our way.  Only Aegis was still in action, and he was hemmed in by the three dogs and Regent's borrowed laser cannon.



Grue stepped out of the darkness near me, holding onto Bitch much the same way I was holding Tattletale.



``Let's scram,'' I said.



``Let's,'' he agreed, in his haunting voice.



``Hey G-man,'' Tattletale winced, ``Pop my shoulder back in?''



Grue nodded.  I helped brace Tattletale as he shoved her arm back into place.  He asked, ``What happened?''



``It was Glory Girl on the roof,'' I explained, then I coughed painfully a few times before adding, ``Can we please get the fuck out of here?''



``You guys took Glory Girl?'' Grue asked, incredulous, while Bitch roused herself enough to whistle for her dogs.



``In a sense,'' Tattletale replied, at the same time I nervously pointed out, ``She could be coming after us any second.''



We got on the dogs, and Regent fired a salvo of shots from the laser cannon into Aegis, hammering him into the side of a building until the wall around him collapsed.  He then paused to jam his taser into the control panel.  When the gun started to smoke, Regent made his way down, jumping the last four or five feet to land on a dog's back.  He tucked the skateboard under one arm.



``Leave it,'' Grue said.



``But--''



``Tracking device.  Assume any tinker worth a damn is going to have tracking devices in their stuff.''



``It's true,'' Tattletale answered, as Regent turned towards her.  ``Sorry.''



``Fuck!'' Regent swore.  He jammed his tazer into the underside of the skateboard like he had with the control panel, then threw it across the street.



We were mounted with Bitch sitting in front of Grue, mainly so he could support her, and Tattletale behind me on Angelica, her uninjured arm wrapped around me.  Regent was alone.



Grue raised his arms, and filled the street with darkness.



Angelica bolted, nearly unseating me, as she made a headlong run into the absolute darkness.  I was on a creature more than twice the size of a horse, without a saddle, and she wasn't suited for riding in the same way a horse was.  I had one foot resting on a horn of bone that jutted from her side, while the other dangled.  My hands were gripping the straps we'd fitted her with, the only thing from keeping me tumbling backwards, head over heels, as she lunged forward at run that would probably outpace any cars on the road.  Not that there would be any cars.  The police and parahuman response teams would have the area blocked off around any potential cape fights.  To make our escape all the more terrifying, I knew the dog couldn't see.  She was following Brutus by scent, and Brutus was going by Grue's directions.  The blind leading the blind.



I should have been terrified, my hands cramping, unable to see or hear, knowing I could tumble off at any second, but I was elated.  Even when Angelica crashed into something hard enough to nearly knock us off, it didn't kill my enthusiasm.  I hooted, hollered and cheered our victory, barely hearing the noise myself as the darkness absorbed it.



We'd done it.  \emph{I'd} done it.  We'd escaped without killing anyone.  The only ones who'd really been hurt at all had been the Wards, Glory Girl and Panacea, and that would be fixed when Panacea came to, for sure.  Any property damage had largely been the fault of the Wards and Glory Girl.  I'd maybe made some enemies, I'd scared some innocent people, but I'd be lying to myself if I said that could've been avoided.  In short, things couldn't have gone better.



Okay, they could have gone a lot better, but the way they ended up?  Pretty damn good, all in all.



Aegis would have climbed out of the rubble by now, flown up for a bird's eye view.  If Grue was doing what we'd planned, he was filling every street and side street we passed with darkness.  Aegis couldn't see where or if we doubled back or what streets we took, so he could only identify our location by the places where fresh darkness appeared.  If he tried to close in to get us, though, we'd be gone by the time he reached us.  All he could do was follow our general location.



Just when I thought I might not be able to hold on any longer, we pulled to a stop.  Tattletale and I slipped off of Angelica.  Someone, probably Grue, pushed a backpack into my arms.  Even working in total darkness, I managed to change into the set of civilian clothes we'd hidden away before we headed to the bank.  I was handed an umbrella and gratefully unfolded it with my stiff hands.



It was tense, waiting in the darkness, with only the feeling of the rain on the umbrella to give me a sense of the world beyond myself and of time passing.



It was a long time before the world came into view again.  Grue said his darkness faded after twenty minutes or so, but it felt like far longer than that.  As the darkness cleared away, I saw Lisa sitting on the steps at the front of a shoe store, holding aleash in one hand and a paper shopping bag in the other.  Angelica, as normal as she ever was, was on the other end of the leash, sitting patiently.  All around us were shoppers and pedestrians, each with their umbrellas and raincoats, looking around with scared expressions and wide eyes.  The sounds were refreshing after the silence of the darkness – falling rain and the murmur of conversation.



Lisa stood, and winked at me as she tugged on the leash to get Angelica following at her side.  We joined the crowd of disoriented shoppers.



Assuming things went according to plan, Alec would be dropped off next, without a dog, and he'd change into civilian clothes the same way we had.  Bitch, Brian and the two dogs would make the final stop at a storage locker near the Docks.  Inside, they would change into their civies, relax for a few hours inside, and leave the money there for the boss to pick up.  After taking a long enough break that the heroes would have abandoned pursuit, they would make their way back much as we were.



``Everyone came out of this unscathed?'' I asked Tattletale in a low voice.  I was sharing my umbrella with her, so speaking together in a kind of huddle wasn't strange looking.



``No injuries or deaths for us, for the heroes or for the bystanders,'' she confirmed.



``Then it's a good day,'' I said.



``A very good day,'' she agreed.



Arm in arm, we walked leisurely through downtown.  Like everyone else, we craned our heads to follow the police cars and PRT vans that were rushing to the scene of the crime with sirens wailing.  Two girls who just finished their shopping, walking their dog.





