





The building housing the local Parahuman Response Team division didn't really stand out. The exterior was all windows, reflective enough to mirror the mottled dark gray of the sky overhead.  Only a shield logo bearing the letters `P.R.T.' marked it apart from the other buildings of downtown Brockton Bay.



Those entering the lobby would find a strange juxtaposition at work.  On the one hand, you could see the various employees in suits, hurrying in and out of the building, talking in groups.  A team of four PRT officers was on standby, each stationed at a different area of the lobby, outfitted in the best equipment money could buy.  All had chain mesh and kevlar vests, helmets that covered their faces, and firearms.  The equipment differed, however, as two of them had grenade launchers hanging from straps on their shoulders with bandoliers of various specialty ammunition across their chests, including a fire extinguishing grenade, an EMP round and various stun grenades.  The other two had what appeared at first glance to be flame throwers; were they to pull the triggers, they would eject a thick, frothing spray of foam, enough to contain all but the strongest and fastest villains.



In stark contrast to this, there was the gift shop that would be thick with youths when school ended, sporting a selection of action figures, posters, video games and clothing.  Four-foot tall pictures of the various Protectorate and Wards team members were placed at regular intervals around the lobby, each backed by bright colors.



There was a cheery tour guide waiting patiently by the front desk, smiling handsomely at anybody who happened to glance his way.  On schedule, he would introduce tourists and children to the PRT offices, the armory, the training area and the parking lot with the parahuman containment vans, showing them what it took to manage the local heroes.  For those willing to pay for the premium tour, wait up to two hours and suffer a PRT squad escort, there would be an additional stop on the tour – a glimpse of the Wards' Headquarters.



As a beleaguered team of young heroes staggered into the lobby, however, there was no tour, only a heavyset woman with a bob.  She wore a navy blue suit jacket and skirt, and waited with a pair of stern looking men in suits just behind her.  Wordlessly, she led them through a door behind the front desk and into a meeting room.



``Director Piggot.  Ma'am,'' Aegis greeted her, his voice strained.  His costume was in shreds, and was more crimson with his own blood than it was its original white.  It was bad enough his civilian identity might have been revealed, if it weren't for the matted blood and the chunks of meat that had been taken out of him, some of the wounds nearly a foot across.



``Good god, Aegis,'' her eyebrows raised a fraction, ``You look like hell.  What's wrong with your voice?''



``Punctured lung, ma'am,'' Aegis rasped, ``I think there's a hole in my front and back.''  As if to demonstrate, he stuck his fingers into his chest cavity.



Director Piggot didn't look away, but one of the men standing behind her looked a touch green around the gills, ``I can take you at your word.  You don't need to stick your arm all the way through your chest to demonstrate.''



Aegis grinned and removed his hand from his chest.



Her expression hardened, ``I wouldn't be smiling right now.''



Aegis' grin fell.  He glanced over his shoulder at his teammates.  Gallant, Kid Win, Vista, Browbeat and Clockblocker were all wearing suitably somber expressions.



``This was a fiasco,'' she told them.



``Yes ma'am.  We lost,'' Gallant admitted.



``You lost, yes.  That's the least of it.  You also caused horrific amounts of property damage.  I'm afraid any and all destruction caused by New Wave's golden child is also your responsibility, since you invited her along.  \emph{Without my say-so.}''



``I invited her,'' Gallant spoke up, ``I'll take the blame, and you can take the costs for the property damage out of my trust.''



Director Piggot offered him a thin and utterly humorless smile, ``Living up to your name, I see?  Yes, I'm sure that's the best way to get the message across.  Your teammates and I know who you are under the mask.  Of everyone here, myself included, you're the one most able to handle a fine of tens of thousands of dollars.''



``I won't deny it, ma'am,'' Gallant choked out the words.



``I'm afraid I'm a believer in punishment, when punishment is due.  Taking money from someone with money to spare is not going to mean anything.  All of you will share the fees between you.  Since I can't touch the trust funds the PRT established for you, I'll have to settle for docking your pay.  Maybe next time, the rest of you can talk Gallant out of inviting his girlfriend along.''



The protests overlapped. ``It was her sister in the bank!  She would have gone in anyways!''  ``I start college next fall!''



Director Piggot simply weathered the arguments and complaints.  A more cynical person might even suggest she enjoyed hearing them.  When a minute or two passed and it was clear she wasn't going to reply or get dragged into the arguments, the young heroes fell into a sullen silence.  She cleared her throat and spoke again.



``Kid Win.  I'm very interested to hear about this weapon you deployed on the battlefield.''



``My Alternator Cannon?''  Kid Win asked, cringing just a bit.



``You'll have to forgive me,'' Piggot smiled, ``The paperwork gets to be a bit \emph{much} sometimes.  Maybe you know where to find the documentation from our military and science teams, for this Alternator Cannon?''



``Christ, Kid,'' Aegis groaned under his breath, with his ruined voice.



Kid Win looked more upset about Aegis' reaction than anything else, ``I, uh.  I didn't get it officially cleared, yet.  I just thought it would be better to use the cannon and do what I could to stop the robbery.''



``That's where you'd be wrong,'' Piggot told him, ``Fact of the matter is, the money that was taken from the bank falls very low on my priority list.  You might even go so far as to suggest I don't care about it.''



``Director--'' Aegis started.  He didn't get to finish.



``What I care about is the public perception of capes.  I care about ensuring that we get enough funding to keep you Wards, the Protectorate and the PRT squads paid and equipped.  Without that, everything I've worked to build falls apart.''



``What are you going to do?'' Kid Win asked her.



``The cannon gets dismantled, first off.''



``No!'' Aegis and Kid Win spoke at the same time.  Director Piggot looked briefly surprised at the defiance.



``I started on the Alternator Cannon so I'd have something to bring out in case of a Class A threat,'' Kid Win said, ``Getting rid of it would be \emph{such} a waste.  I don't care if I never get to use it again.  Give it to your PRT squad.  I'll teach someone how it works.  You can mount it on one of your trucks or something.''



Director Piggot frowned, ``The amount of time and money that would require, for an event that might never occur\ldots no.  I suppose you can keep the cannon.''



Kid Win practically sagged with relief.



``But whatever the power source is, you're removing it, and I'm keeping it under lock and key.  If a Class A threat does come into play, I'll hand it over to you.  \emph{And} the cannon still goes through the standard review process for all Tinker created material.  If it doesn't pass the review, if you were putting people and property at undue risk with what you pulled today, I'm afraid you could face a substantial fine or jail time.''



Kid Win paled.



``Director!'' Aegis grunted out the word, taking a step forward.



``Be quiet, Aegis,'' Piggot snapped, ``Your trying to speak with a punctured lung physically pains me, and as much as I admire standing up for your team, your one lungful of breath is wasted here.''



Kid Win turned to Aegis and offered a small apologetic smile.



``Kid Win, you're coming with us for a disciplinary review.  Everyone else is dismissed.  The tour group is going to be coming by your quarters in an hour, and there's likely to be more than a few reporters peering in the window.  Try to clean yourselves up for the pictures that are undoubtedly going to appear in tomorrow's papers.  Please.''



The two men in suits marched a miserable Kid Win out the door after Director Piggot.  Kid Win shot a worried look at his team before he was taken out of sight.



``We debrief,'' Aegis grunted, ``Gallant or Clockblocker handles it.  You two decide.''



The team trudged out of the meeting room and made their way to their reserved elevator.  It was Tinker-designed to impress the tourists as well as be far more secure.  Interlocking sections of metal unfolded and slid apart as they approached, then closed behind them.  The ride down was so smooth that it was nearly impossible to tell the elevator was moving.



They exited into a long corridor of chrome steel.



``I'm going to have nightmares,'' Clockblocker groaned, as he tenderly touched the welts around his nose and mouth, ``Nightmares with lots and lots of spiders.''



At the far end of the corridor, they came to a security terminal.  Aegis pointed at Clockblocker.



``Don't you usually do it?''



``Retina maybe detached,'' Aegis admitted in his halting voice, ``Don't want to fail scan.''



Clockblocker nodded hesitantly, then leaned forward to let the terminal scan his eyes.  Steel doors clicked, then whisked open with a barely audible whirr, letting the young heroes and heroine make their way into the main area of their headquarters.



The room was roughly dome-shaped, but there were sections of wall that were able to be dismantled and rearranged on the fly.  Some had been set up to give the various team members their individual quarters, while others framed the doorways that led into the showers, the filing room and their press/meeting room.  A series of computers and large monitors were networked at one side of the room, surrounded by a half-dozen chairs.  One of the monitors was displaying a countdown to the next tourist group, while others were showing camera images of key locations in the city.  The Central Bank was one of them, a dark image punctuated by the red and blue of police sirens.



``Shadow Stalker is AWOL?'' Gallant asked.



``Couldn't make it in time,'' Aegis grunted, ``Told her to stay put.''



``She's going to hate that.  Doesn't she have this huge hate-on for Grue?'' Clockblocker asked.



``Part of the reason,'' Aegis grunted out the words, ``I told her to stay.  Don't need that.  I'm going to shower.  Patch myself up.  You guys debrief.''



``Sure thing, Chief,'' Clockblocker saluted.  ``Take care of yourself.''



``Fucking mutant dogs,'' Aegis muttered, as he made his way to the bathroom.  He was stripped out of the top half of his tattered costume before he was through the door.



``Vista?  Can you go grab the whiteboard?  Grab two?'' Gallant turned to their junior member.  Vista almost skipped in her rush to follow the order.



``What's going to happen to Kid?'' Browbeat spoke up for the first time, ``I don't know how all this goes.  Is it serious?''



Gallant considered for a moment, ``Could be, but my gut tells me Piggy just wants to scare him.  He needs to stop testing the limits with the people in charge, or he's going to get in real trouble at some point.''



``So, not exactly the best start to your new career, huh?'' Clockblocker turned to Browbeat.



``Fuck, I wouldn't mind so much if I knew what happened,'' Browbeat stretched, and his muscles began to dwindle in size, ``At least then I could figure out what to do better next time.  All I know is that I was suddenly blind and deaf, and when I tried to move, everything bent the wrong way.  Then I think I got tasered.''



Vista returned, dragging a pair of whiteboards on wheeled frames behind her.



``Hold that thought,'' Gallant told their newest member, ``Hey Clock, you don't mind if I take point?''



Clockblocker was still using his fingertips to explore the raised bumps on his face, ``Go for it.  I'm going to procrastinate as long as I can on the leadership thing.''



``You're next oldest, after Carlos.  It's only going to be what, three or four months, before you're the senior member?''



``And I'll hold that position for not even the rest of the summer before I graduate and pass the mantle to you,'' Clockblocker smiled self deprecatingly, ``No worries.  Take charge.''



Gallant took off his helmet and held it in one hand, running his fingers through his sweat-damp blond hair.  He smiled winningly at Vista as she positioned the whiteboards so everyone could see them, ``Thank you.''



Gallant didn't need to use his power to get an emotional response from the thirteen year old heroine.  She turned a bright pink.  There could be no doubt for anyone present that she had a major crush on her senior teammate.



``Okay guys,'' Gallant said, ``Before we get started, I think it's important to make some things clear.  First off, most importantly, today was not a failure.  I'd even say that today was a win for the good guys, and we start establishing that here and now.''



He took a second to gauge his audience's disbelieving reactions, then smiled.



``The Undersiders.  They've flown under the radar so far, but more recently, they've started pulling higher profile jobs.  They hit the Ruby Dreams casino five weeks ago, and now they just robbed the biggest bank in Brockton Bay.  This time we were lucky enough to get in their way.  That means we finally have intel on their group.''



He turned to the whiteboard and wrote the names of their opponents.  Grue, Tattletale and Hellhound went on the first board, with lines separating the board into three columns.  He wrote Regent on the second board, drew a line and then hesitated at the fifth and last column.  ``Did he name himself?  The guy with the bugs?''



``Girl,'' Clockblocker corrected him, ``I was talking to the hostages after the Undersiders made their getaway.  He said he was afraid to move because \emph{she} was going to make it bite him.  It took me a bit to realize exactly what he meant.  Poor fella was in shock.''



``But we don't know what she called herself?''



Nobody had any answer to that.



``Then we need to agree on a name for her, or the paperwork's going to be inconsistent.  Suggestions for a name for the bug girl?''



``Maggot?  Worm?'' Browbeat offered, ``Stick her with a crappy name?''



``We don't want to do that,'' Clockblocker sighed, ``Maybe if we'd won, we could get away with it, but it doesn't look so good if the press reports that we got our asses kicked by someone called maggot.''



``Stinger, Pestilence?'' Vista suggested.



Clockblocker spun himself around in the chair and punched the names into the computer, ``Taken.  Stinger is some villain in California with power armor, a jetpack and homing missiles, and Pestilence is a creepy psycho in London.''



``Skitter?'' Gallant put the name out there.



There was a clatter of keys as Clockblocker checked, ``It's not taken.''



``Then it's good enough,'' Gallant wrote the name up on the whiteboard, ``Now we brainstorm.  This is where we recoup our losses from the day, figure out an angle so we can win next time.  So don't hold back.  Share any detail, no matter how insignificant.''



``Grue's power isn't just darkness.  You can't hear in there either.  And it feels strange too,'' Browbeat spoke, ``There's resistance, like you're underwater, but not floating.''



``Good,'' Gallant wrote that in Grue's column, ``Next?''



``The mutants that Hellhound makes.  The dogs?  She doesn't control them with her mind.  They're trained,'' Vista offered, ``She tells them what to do with whistles, gestures.''



``Yes, good, I noticed that,'' Gallant replied, excitedly adding another note to the whiteboard.



``The girl with the bugs\ldots Skitter.  It's just the opposite.  She has a \emph{lot} of fine control over them,'' Clockblocker added.



``Yes!''



``Also, according to the hostage I talked to, she said she can sense things through her bugs, which is how she kept an eye on the hostages.''



It wasn't long before most columns were full enough that Gallant had to turn the whiteboards around to use the backs.



Carlos returned from the shower, wearing sweatpants and a towel around his shoulders.  He was Puerto Rican, his hair long.  His body was clean of blood, barring a few residual trickles from the mess of ragged wounds on his arms, stomach and chest.  He had clumsily stitched the cuts and gouges together, which did surprisingly little to make them easier to look at.  He sat down on a chair and added his input for the lists, which didn't amount to too much.  He had been incapacitated for too much of the fight to have much to say.



There was an abrasive noise from the computer as every monitor suddenly flashed yellow.  The Wards hurried to pull on their masks.  Aegis grabbed a spare from a drawer by the computers.



The entrance whirred open, and Armsmaster strode in, accompanied by the winsome Miss Militia.  She wore a modified military uniform, tight enough in the essential areas to accentuate her curves, sporting a scarf around her lower face with an American  flag embroidered on it, and a similar sash around her waist.  Most arresting, however, was the large rocket launcher she held across her shoulders in the same way a weightlifter might hold a barbell.



``Armsmaster,'' Gallant stood up, ``Good to see you, Sir.  Miss Militia, always a pleasure.''



``Ever the gentleman,'' Miss Militia's eyes hinted at the smile behind her scarf, ``We brought a guest.''



Following behind Armsmaster and Miss Militia was a teenage girl in an enveloping white robe.  Panacea.  She had an ID card on a cord around her neck, featuring her photo and the word `GUEST' in bright blue letters.



``She was kind enough to volunteer to come here and patch you guys up,'' Miss Militia told the young heroes, ``Can't send you home with horrible injuries and hundreds of bug bites, can we?  That would give away the show.''



She shifted the position of the rocket launcher on her shoulders, and it dissolved into a blur of green-black energy.  The energy lunged and arced around her for a few brief moments, then materialized into a machine gun.  It only held that form for a few seconds before it flickered and solidified into a sniper rifle, then a harpoon gun, and  finally settled in the form of a pair of uzis, one in each of her hands.  She barely seemed to notice, beyond the automatic action of holstering the guns.



``I wanted to thank you guys for coming to my rescue,'' Panacea spoke, shyly, ``And for letting Glory Girl come with you.''



Gallant smiled, then in a more concerned tone, he asked, ``You two are okay?''



Panacea shook her head, ``Tattletale found a way around my sister's invincibility.  Glory Girl was bitten pretty badly, which is why I didn't come sooner.  I think it hits you harder, psychologically, when you're pretty much invincible but you get hurt anyways.  But we're okay now.  She's healed but sulking.  I- I'm alright.  Bump on my head, but I'm okay.''



``Good.''



Armsmaster was at the whiteboard, going over the points.  ``I like this.  But this one\ldots''  He tapped the column titled Tattletale, ``Nearly empty.''



``None of us ran into her, and the hostages didn't have anything to say about her,'' Gallant replied.



``Panacea may be able to help there,'' Miss Militia offered.



All eyes turned to the girl.



``I- A lot happened,'' Panacea hedged.



``Any detail helps.''



``Um.  I'm sorry,'' she said, looking down at the ground, ``I got smacked across the head, but my power doesn't work on myself, and I'm not really the type to go out in costume and get into fights, so having my life threatened, I dunno.  All that\ldots I can't put my thoughts in order just yet.''



``The sooner--'' Armsmaster started.



``It's fine,'' Miss Militia interrupted him, ``Amy, why don't you start taking care of the Wards?  If something comes to mind, anything the Undersiders said or did, or any clues you think might help, share it afterwards, alright?''



Panacea smiled gratefully at the heroine, then turned to the group, ``Who needs the most help?  Aegis?''



``I'll live,'' Aegis said, ``I can be last.''



Gallant hesitantly raised his hand, ``One of Hellhound's dogs slammed into me.  I think I might have a broken rib.  Paramedics cleared me, but I want to be extra sure I'm not risking a punctured lung or something.''



Panacea frowned, then gestured to the far end of the room, ``I'll take a look at you over there?''



``Go figure, Glory Girl's boyfriend gets special treatment,'' Clockblocker grinned to make it clear he was just poking fun.  Gallant just smirked in response.



The pair went to Gallant's alcove, and she sat him down on the bed before laying a hand on his shoulder.  She pulled her hood back and furrowed her brow.



``You don't have a punctured lung.  You've got one fractured rib, but you're not even in that much pain.  Why--''



``I lied.  I wanted to talk to you, alone,'' he took her hand.



She scowled and pulled her hand back like he'd bitten her.  As if to make doubly sure he wouldn't grab her hand again, she folded her arms.



``You know I can sense emotions,'' he said, ``Everyone's emotions, like a cloud of colors around them.  Can't turn it off.  It's just how I see the world.''



``Victoria mentioned that.''



``So you're an open book to me.  I know you're scared.  No\ldots you're terrified, and that's why you're not talking.''



She sighed and sat on the bed, as far from Gallant as she could.



``I never wanted these powers.  I never wanted powers, period.''



He nodded.



``But I got them anyways, and I got international attention over it.  The healer.  The girl who could cure cancer with a touch, make someone ten years younger, regrow lost limbs.  I'm \emph{forced} to be a hero.  Burdened with this obligation.  I couldn't live with myself if I didn't use this power.  It's such an opportunity, to save lives.''



``But?''



``But at the same time\ldots I can't cure everyone.  Even if I go to the hospital every night for two or three hours at a time, there are thousands of other hospitals I can't visit, tens of millions of people who are terminally ill or living in a personal hell where they're paralyzed or in constant pain.  These people don't deserve to face that, but I can't help them all.  I can't help one percent of them if I put in twenty hours a day.''



``You have to focus on what you \emph{can} do,'' Gallant told her.



``Sounds easier than it is,'' Panacea answered, with a touch of bitterness, ``Do you understand what it means, to cure some of these people?  I feel like every second I take to myself is a second I've failed somehow.  For two years, it's been this\ldots pressure.  I lie in bed, awake at night, and I can't sleep.  So I get up and I go to the hospital in the middle of the night.  Go to pediatrics, cure some kids.  Go to the ICU, spare some lives\ldots and it's all just blending together.  I can't even remember the last few people I saved.''



She sighed again, ``The last person I really remember?  It was maybe a week ago, I was working on a kid.  He was just a toddler, an immigrant from Cairo, I think.  Ectopia Cordis.  That's where you're born with your heart outside your body.  I was putting everything in the right place, giving him a chance at a normal life.''



``What made him so memorable?''



``I resented him.  He was lying there, fast asleep, like an angel, and for just a second, I considered just leaving him.  The doctors could have finished the job, but it would have been dangerous.  He might have died if I'd left him on the table, the job half done.  I hated him.''



Gallant didn't say anything.  Scowling, Panacea stared down at the ground.



``No, I hated that he would have a normal life, because I'd given up mine.  I was scared that I might \emph{intentionally} make a mistake.  That I might let myself fuck up the procedure with this kid.  I could have killed him or ruined his life, but it would have eased the pressure.  Lowered expectations, you know?  Maybe it would have even lowered my own expectations for myself.  I\ldots I was just so tired.  So exhausted.  I actually considered, for the briefest moment, abandoning a child to suffer or die.''



``That sounds like more than just exhaustion,'' Gallant replied, quietly.



``Is this how it starts?  Is this the point I start becoming like my father, whoever he was?''



Gallant let out a slow breath, ``I could say no, that you're never going to be like your father.  But I'd be lying.  Any of us, all of us, we run the risk of finding our own way down that path.  I can see the strain you're experiencing, the stress.  I've seen people snap because of less.  So yeah.  It's possible.''



``Okay,'' she said, just under her breath.  He waited for her to elaborate, but she didn't.



``Take a break.  Tell yourself it's something you have to do, to recharge your batteries and help more people in the long run.''



``I don't think I can.''



They sat in silence for a few moments.



He turned towards her, ``So what does this have to do with what happened at the bank?''



``She knew everything.  That Tattletale girl.  She said she's psychic, and from what she said, what she knew, I believe it.''



Gallant nodded.



``You know what it's like, to talk to people like her?  Like you, no offense?  You build up this mask, you delude yourself into thinking everything is normal, and you force yourself to look past the worst aspects of yourself\ldots and then these Gallants and Tattletales just strip you naked.  Force you to confront it all.''



``I'm sorry.''



``You said yourself, you can't turn it off, right?  Can't really blame you.  It's just\ldots it's hard to be around.  Especially after dealing with Tattletale.''



``What did she say?''



``She threatened to talk about stuff.  Stuff worse than what I just told you, I guess.  Threatened to tell me things I just don't want to know.  Said she'd use what she knew to ruin my relationship with Victoria and the rest of my family,'' Amy hugged herself.



``My sister's all I've got.  The only person with no expectations, who knows me as a person.  Carol never \emph{really} wanted me.  Mark is clinically depressed, so as nice as he is, he's too focused on himself to really be a dad.  My aunt and uncle are sweet, but they've got their own problems.  So it's just me and Victoria.  Has been almost from the beginning.  That smug little monster threatened to tear my sister and I apart using yet another thing I didn't want, another thing I had no control over.''



Gallant started to speak, then stopped.



``What?''



``Does\ldots does this have anything to do with the, erm, rather strong feelings you have towards me?''



Panacea went still.



``I'm sorry,'' he hurried to say, ``I shouldn't have brought it up.''



``You shouldn't have,'' she stood up and started towards the door.



``Look, if you ever need to talk\ldots'' he offered.



``I--''



``You probably won't want it to be me, okay.  But my door's always open, and you can call me at any hour.  Just letting you know.''



``Okay,'' she replied.  Then she reached over to him and touched his shoulder, ``There.  Bruises gone, ribs touched up.''



``Thank you,'' he replied, opening the door for her.



``Take care of my sister, okay?  Make her happy?'' she murmured, as she hesitated in the doorway.



``Goes without saying.'' They rejoined the main group.



Every head in the room turned as Panacea picked up the marker by the computers.  With a grim expression on her face, she began filling in Tattletale's section of the whiteboard.





