





``Weaver,'' the voice had a slight digital twang at the edges, to the point that I thought it was Bakuda for a second, even if the two voices were entirely different.



I lowered my book.  Defiant stood in the doorway to my cell, flanked by two of the prison guards.



I swung my feet to the ground, simultaneously sitting up.  ``If you'd asked me a few weeks ago, I'm not sure I would have believed that I'd actually be happy to see you.''



``You'll be coming back,'' he warned me.  ``This is a temporary leave.''



``I know,'' I said.  I marked the page in my book, placing it in a corner, where it joined twelve others.



``And yes, I'm not surprised you had hard feelings.  We weren't on good terms then, and even now\ldots''



He didn't finish the sentence.  \emph{Even now, we aren't friends?}



``A lot of books,'' he noted the stack of prison library books.  ``You've read them all?''



``Yeah.''



``In seven days?''



``Lots of time to myself.  I don't have classes, but I have homework and self-study, and that cuts into reading time, or I'd have read more.  But it's kind of nice, if you ignore\ldots pretty much everything else.  I've had time to think for the first time in months.''



``I know what you mean,'' Defiant said.  ``I remember worrying every day if that would be the day innocents were caught in a crossfire between Coil and Kaiser, or the day a member of Empire Eighty-Eight was initiated into the group, with the requisite assault of an `acceptable target'.''



I grimaced at that.  He extended an arm, indicating I was free to leave the cell.



He continued as we walked, flanked by the guards.  ``\ldotsAnd then there was the team, handling the internal politics, Assault's harassment of Battery, the Wards and their individual issues.  The countless requests for appearances, for photo shoots, interviews, and demonstrations, figuring out which have to be accepted, which can be turned down, knowing that too many refusals in a row could mean a negative article.  And then there were the threats, of course, dealing with powered criminals.  Every team member becomes a resource, and those resources have to be allocated judiciously.''



``And in the midst of all that, you're still trying to find time for \emph{you},'' I said.



``Free time is the easiest thing to sacrifice,'' Defiant said.  ``It costs you, to give it up, but there's little guilt.  Time to yourself is best spent preparing.  Developing new technology, strategizing, adjusting equipment-''



``Weaving costumes, pre-preparing lines of silk,'' I said.



Defiant nodded.



``I may have inadvertently screwed Miss Militia over,'' I said.



Defiant shook his head.  ``She's a natural leader.  I wasn't.''



``That might make it easier to handle,'' I said, ``But she'll still be in a position where she has to worry, has to prioritize and make sacrifices, and I don't know if she asked for it.''



``She'll manage,'' Defiant said, as if that was that.  I couldn't tell if it was trust in his teammate or if he wasn't particularly empathetic on that front.  Miss Militia \emph{was} the one who'd supplanted him as team leader.  Were there still hard feelings?



We stopped at the end of the hallway, and the guards stopped to check in at the control station that managed which doors opened and when.  There were procedures for seeing a prisoner out, and it took some time.



I could see into cells near the gate.  Prisoners glared at me.  I was a villain to everyone who had a grudge against supervillains, a hero to everyone who had a grudge against `cops'.  A traitor.  A murderer.  The person who'd killed one of the strongest heroes in the world.  Who'd killed someone who had fought for \emph{decades} to save the world, again and again, and who may have doomed us all.



The other prisoners were still trying to assess me, I was pretty sure.  Nobody spoke to me or approached me when we filed off to get our meals or when I visited the library.  The words printed on my uniform were probably daunting for the unpowered.



The judge had seen fit to assign me to a close security prison, a wing in a medium security facility.  It was somewhat backwards, as rulings went, everything taken into consideration.  I'd been charged as an adult, for one thing, so juvenile detention was out.  Too many crimes under my belt.  I was apparently too dangerous for a minimum security institution, but the PRT had asked for leniency, and this was the compromise they'd come to.



As far as I could figure it out, it was everything I might have expected from a medium security prison, complete with a station that controlled the opening and closing of cell doors, constant supervision, and escorts wherever we went.  The only difference was the emphasis on \emph{programs}.  We were here to be rehabilitated, to find work, get an education and get therapy.  All mandated.



I'd already started studying.  Now, with Defiant here, I'd get okayed to start other projects.  I hoped.



The warden was waiting for us in the `hub', the room with benches where we'd waited to be assigned to our cells.  She wasn't what I'd expected from a person in charge of a prison.  She made me think of a stern teacher, instead.  She was old, pushing sixty if not well past it, and ramrod straight, and thin.  Her graying hair was tied back into a short braid that didn't quite reach the bottom of her neck.  She was tough in a gnarled, craggy sort of way, like the veteran actors of cowboy movies, but female.



``Taylor Hebert,'' she said.



``Ma'am.''



``Every rule in my prison applies while you're outside.  You know this.''



``Yes, ma'am.''



``I know you capes are magnets for trouble.  If a fight happened to erupt while you were en route and it came down to you fighting back or getting stabbed, I expect you to get stabbed and then graciously \emph{thank} your attacker, you understand?''



``Yes ma'am.''



``That said, best if you don't get hurt.  Running would be preferrable, so long as you don't \emph{run}.  Trying to escape would be the worst thing you could do, and it wouldn't succeed.''



``You want me to stay out of trouble.  I understand, ma'am.''



``It's a cushy deal you have here, but \emph{one word} from me, and that changes.''



``I get that, ma'am.  Really, I do.  I \emph{get} that I did some sketchy things.  I get that this is a kind of penance, probably not as harsh as I deserve, and I welcome it.  I think, given a choice between walking away free right this second and continuing my sentence, I'd choose the latter.''



She studied me for long seconds.



``We have a no-tolerance policy on powers, Ms. Hebert.''



``Yes ma'am.''



``What appeared to be an emerging case of body lice in the main prison seems to have abruptly corrected itself, according to our physicians.  The roach traps in the kitchen aren't catching anything, either.''



``Yes ma'am.''



``There's a part of me that would like to think you're doing us a service, cleaning things up.  Which would still be a violation of the zero-tolerance rules, but somewhat forgivable given the intent.  Another part of me has to be concerned that you're hoarding these in the same manner another prisoner might hoard makeshift weapons.''



``No, ma'am.''



``Which is it?''



``I sort of hoped to talk about it with my therapist, on our first meeting, and figure out the best way to approach it before talking to you.''



She made a `continue' gesture with her hand, arms still folded, her gaze hard.



``My power is always on.  It takes a conscious effort to block them out and let them act normally.  I feel what they feel, sense what they sense, sort of.  It's\ldots not fun with lice, crawling around in prisoner's pubic hair, you know?  Being aware of that, across eighteen, nineteen prisoners, twenty-four-seven?''



``My concern, Ms. Hebert, is what you're doing with those bugs.''



``Nothing,'' I said.  ``I- moved them away from the prisoners.  I've mostly left them where they were, let them starve.  I can't leave them stationary like that where there are rodents, or they'll only feed the rodent population and you'll have a bigger problem.  I could \emph{kill} the rodents, but then you'd have dead rats in your walls, and-''



``This isn't acceptable.  You understand why this isn't acceptable?''



``You have to protect other prisoners,'' I said.



\emph{Even if it means letting them have lice?  }I didn't say that last part.



``If bugs are your weapon of choice, I can't let you have access to them.''



``What about a bucket?'' I asked.



``Hm?''



``Set up a bucket in some back room, fill it with something caustic enough to kill them on contact.  I'll drown every bug I can reach in the bucket, and you'll be able to see for yourself, by the volume of bugs that are in there.''



``Let's postpone measures like that,'' Defiant cut in.  ``Go change.''



I nodded, happy for the escape route.  I made my way to the combination shower-and-change room area, pausing to collect my civilian clothes from the guard in the bulletproof glass enclosure that overlooked the hub.



I would have liked to shower in relative privacy, but I didn't think anyone outside was planning on waiting.  I stripped out of the prison uniform, a lightweight, gray one-size-fits-all cotton tunic and pants that felt more like pyjamas than real clothes.  Mine weren't as threadbare as the clothes the other prisoners wore.  For one thing, I was a `small'.  Sort of.  It was a choice between either wearing a medium-sized tunic and have it hang around me like a tent, or wear a small and have it barely reach my beltline.  I'd chosen the latter.



The \emph{other} reason I got a uniform that hadn't been worn a hundred times by a hundred other prisoners, was that I wore a special prison uniform with `Sp. Inmate' printed across the shoulders and sleeve, informing everyone who saw me that I had powers.



After folding the garments, I donned my `Weaver' costume.  I'd have to update it.  It wasn't real, wasn't fit for fighting.  The underlying bodysuit was something generic they kept on hand, no doubt similar to what made up Clockblocker's costume.  Much in the same way his costume had been elaborated on with armor panels, mine had armor that Dragon had 3D-printed prior to arriving at the PRT headquarters.



It felt wrong, especially the way the straps fit into it, and I didn't like knowing how flimsy it was.



I didn't wear the mask or the armor panels, merely holding the bundle that contained them.  Instead, I pulled on clothes over the bodysuit, rolling up the sleeves until they were midway up my biceps.  The same short-sleeved, button-up shirt I'd changed into after we'd met with the judge, and jeans.



When I emerged, Defiant and the warden were talking.  She had enough presence that even Defiant, six feet tall and clad in armor, looked like he wanted to back down.



She tapped him in the center of his chest to punctuate her words, ``\ldotsbefore lockdown.  And I want all paperwork, as soon as you get it.''



``You'll have it,'' he responded.



``Hand out,'' the warden said, turning to me.



I extended a hand.



She strapped a device to my wrist, like a pager, but with a coarse black strap attached.  ``So we know where you are.''



``Okay.''



The warden looked to the guard in the bulletproof glass enclosure.  She gave him a hand signal, and he opened the front door to the prison.



We made our exit down a corridor of double-layered fences topped with barbed wire.  We entered the parking lot, where a small crowd had gathered around Defiant's ship, staring.



They parted to let us board, and then backed away as the jets started to thrum with life.



``We're alike in some ways,'' Defiant said, from his seat at the controls.  I sat behind him, having belted myself in.



My response was cut short as we started moving, and inertia hit me like a pressure  wave against the front of my entire body.  I managed only a ``Hm?''



``We've both been leaders.  We've both made our mistakes, and we've faced a form of detention for it.  You with your prison, me with my \emph{retirement}.''



Oh, he was back to that?  We'd been interrupted.



``Guess so,'' I managed.  ``And Dragon?''



``Not a leader,'' Defiant answered me.  ``Not unless you count the artificial intelligences that operate the other suits.  But her prison?  It remains worse than any you or I have faced.''



``Remains?''  I asked.



``Yes,'' he said, but he didn't elaborate.



How could her prison be worse than jail?  And how could she still be in it, unless\ldots was she disabled?  Cerebral palsy, partial or total paralysis, something else?



I wasn't sure how that factored in with her current inability to communicate.  If she relied on a computer to speak for her, maybe something in the program had broken?



The craft changed direction.  Defiant tapped a button, then let go of the controls.  Autopilot?



``Whatever happens,'' he said, ``You're a member of the Wards.  That's done, but the nature of your membership is still very much in question, understand?''



``I'm not sure I do.''



``Before, I mentioned the tasks of being in charge of a Protectorate team.''



``Allocating people.''



``Yes.  Today you're going to meet some people who are going to play a very crucial role in deciding how you are allocated.  Best case scenario, we put you on a team in the thick of something.  Not the quiet you've been enjoying in your cell, but you'd be helping.  Everyone benefits.''



``And the worst case?''



``The worst case is they say it's a mistake, and you go to jail for the foreseeable future.  I don't see that happening.  The second-to-worst case is more likely, where there are no team leaders willing to take you on board with all of the inherent risks.''



``You just said I was a member of the Wards.''



``I did.  Miss Militia has your back, but there's no way you could join the Brockton Bay Wards, under her.  Conflict of interests, animosity\ldots''



``I figured.''



``Chevalier's interests are in restoring the PRT and Protectorate programs.  We've committed to helping in any world-scale crisis events, which means participating in the next Endbringer program.  He respects Miss Militia's opinion, and your appearance before the media means we've committed to keeping you.  That was partially intentional.''



``Intentional?''



``Because it throws a wrench in the plans of anyone who might want to maintain the status quo.  But as much as Chevalier is on your side, if the capes directly under him in the command structure deem it necessary, he could easily send you to a place where you couldn't do any damage and bring you out of hiding for media appearances and Class-S threats.''



``A place where I couldn't do any harm?  Like?''



``Guard duty at the quarantine area in Madison, perhaps, or a town without a cape presence, where you'd be doing little more than making appearances and talking to kids.''



``I'm\ldots I don't want to sound arrogant, but I'm better than that.''



``Mm hmm,'' he said.  ``Let's hope they think so.''



He pressed the button and took hold of the controls.  ``New York.  The central headquarters of every Protectorate team in America.''



\sectionbreak



With Defiant beside me, my civilian clothes removed, costume donned, I entered the common room of the local Protectorate team.



The interior wasn't dissimilar from the Wards' headquarters in Brockton Bay.  I'd visited that spot when we'd stolen the data from their server.  The layout was similar, with what seemed to be interchangeable or connecting pieces defining the interior.  The difference was in the \emph{quality} of the pieces.  Gold or faux-gold trim marked pillars and short walls.  There wasn't any brushed steel or ceramic.  It was \emph{marble}.  This would be where they held the interviews and wowed the people who invested in the merchandising side of things.



Inspiring, in a way.  Intimidating.



Equally intimidating, if not more so, was the crowd that waited for me.  Eleven people, arranged across the room, most of them capes.



``In the lead, we have Prism, second in command of the New York team,'' Defiant told me.



Prism's lips flattened into a tight line as she looked at me.  We'd met, at the Mayor's house.  She'd been one of Legend's people.  I supposed that Chevalier would have wanted someone who knew the city and the routines as his second in command.



``Rime, team leader of Los Angeles,'' Defiant said.



\emph{Taking over for Alexandria}, I thought.  A cape with black hair in a blue skin-tight costume with fur.  I recognized her from the Echidna event, the cape who made ice crystals.  I remembered how she'd been following Chevalier's orders.  His second in command?  It made sense he'd promote someone he knew to the second largest team in America.



``Revel, team leader of Chicago.''



Revel was a woman I hadn't seen before, even in the background of the various Class-S fights.  I was pretty sure I would have recognized her.  She was clearly Japanese, with a painted mask covering her lower face, and a massive lantern on a stick that rested against one shoulder.  She wore a white skin-tight outfit with straps at the shoulders, the legs ending mid-thigh, giving her a degree of modesty that the stylized crimson kimono didn't.  The kimono hung loose around her, held in place more by belts and what must have been wires in the fabric, elbow-length and just barely long enough to be modest.  Her shoulders were bare and narrow, her expression\ldots one eyebrow was raised as she studied me.



``Dispatch, the second in command of Houston.''



Prism at least had an apparent reason to dislike me, but Dispatch's expression suggested he'd come to that conclusion all on his own.  His costume was white, with steel points rising from his shoulders and either side of his brow.  The mask that covered the upper half of his face was sculpted into a perpetual frown.  I might not have given it a second thought, but his mouth\ldots the frown left me little doubt he didn't like me, right off the bat.



``You may recognize some of the captains of the respective Wards teams.  Jouster from New York, Vantage from Los Angeles, Tecton from Chicago and Hoyden from Austin.  You know Clockblocker.''



I nodded.  Tecton, in what looked to be a fresh outfit of bulky rust-red power armor, gave me a salute.  Jouster was playing up the medieval theme, a spear in hand, while Vantage was a black guy in forest green and silver\ldots his costume looked a touch flamboyant, at a glance.  Hoyden looked more like a desperado than a superhero, with a costume that incorporated a kerchief with eyeholes over the upper half of her face, her blond curls tumbling behind, and a jacket and jeans in what looked like black-painted chainmail.



Clockblocker leaned against a desk, unreadable.



``Mrs. Yamada, you've met, if the records are right.''



I nodded at the Japanese woman in a casual dress-suit who was standing beside Revel.



``And I'm Glenn Chambers.  PRT head of Image,'' a man spoke.  He approached me to offer a fat hand for me to shake.  He had a firm grip. Glenn didn't look like someone who was particularly invested in image.  He was obese, his clothes not flattering, his hair not quite cut into a mohawk, but gelled into something resembling one.  He wore rectangle-framed glasses that made it easier to see how he seemed to perpetually squint – a result of long eyelashes.



``And I suppose I'm Weaver,'' I said.  Eleven sets of eyes, all on me, judging me.  I hooked my thumbs into my pockets.



``I'm surprised Chevalier hasn't shown up,'' Defiant commented.  He glanced at Prism.



It wasn't Prism who answered.  Dispatch, the Texan cape, spoke instead.  ``I asked the same question.  He brings us all the way here, but he doesn't show himself?''



``He's handling a small crisis,'' Prism said.



``We're all handling crises,'' Dispatch said.  ``Half of us have no experience as team leaders, we're dealing with capes in mourning, with government capes auditing our team rosters for Cauldron capes-``



``Leave it be, Dispatch,'' Rime interrupted him.  ``We should get down to business.  The sooner this is settled, the sooner we can get back.''



Mrs. Yamada cleared her throat.  ``What are you thinking, Weaver?''



\emph{Suddenly put on the spot}.  ``Honestly?''



``Honesty is good,'' she said.



``I'm intimidated,'' I said\emph{.}



``How do you usually handle something like that?''



\emph{By being more intimidating in exchange}, I thought.  It wouldn't do to say that out loud, to explain how I'd fallen back on being scary and ruthless for so long that I wasn't sure how to approach something like this.



``I'm not so sure anymore,'' I said.  It was the truth, and it wasn't self-incriminating.



Mrs. Yamada nodded.



Defiant spoke , ``Let's ensure we're all familiar with what's going on. We've had capes with criminal backgrounds join the Protectorate and Wards teams, though that has remained largely discreet, and Weaver's civilian identity is public knowledge.  We've had experienced capes join, as well, forcing us to adapt to their experience and retrain them where necessary.  Weaver is both.  She's currently serving time in Gardener.  Under the terms of her sentence, she'll be continuing her high school studies independently, she'll be getting therapy as soon as we've settled on a schedule, and she'll be ferried out to various teams for testing and evaluation.''



``A lot of hassle for a little girl,'' Jouster said.



\emph{A little girl?}  I kept my mouth shut, but it took some effort.



Clockblocker, however, was chuckling.



``What?'' Jouster asked.



``She beat Alexandria,'' Hoyden said, ``He's laughing because you're putting down the girl who killed Alexandria.''



``Not a selling point,'' Hoyden's boss, Dispatch, cut in.



``She's an absolute nightmare to fight,'' Clockblocker said.  ``I've been on the receiving end enough times to know.  So when Miss Militia told me she was in custody, I started asking questions, trying to get a sense of what was happening and when.  I don't even have to be here, and I'm picking up extra patrols later this week to make up for it, but I wanted to come and say this:  I don't like her, not really.  But if my word counts for anything, as someone who's only spent half the time dealing with the shit in Brockton Bay that she has?  We want her on our side.  Somehow, in some form.  Because the alternative \emph{sucks}.''



``Thank you,'' I said, my voice so quiet I wasn't sure everyone heard me.  He was standing up for me, in a way, at a point in time I wasn't sure how to voice those sorts of things myself.



I could see Jouster's eyes behind his helmet, as he gave me a once-over.



``She killed Alexandria,'' Hoyden said.  ``And, what, she was there for Leviathan, she was there for the Slaughterhouse Nine, for Echidna\ldots''



``She went head to head with each of those,'' Clockblocker said.  He looked at me.  ``Right?  Like, you weren't just \emph{there}.  You were in the thick of it, exchanging blows?''



I nodded.



``Today is numbers,'' Prism said.  ``Power evaluation, interviews.''



``No, no,'' Dispatch said, shaking his head.  ``Ridiculous.  You don't invite us here, then make us sit through that nonsense.''



``We need to evaluate her abilities,'' Defiant said.



``Do it on your own time.  And skip the interview,'' Dispatch said.  ``Your own notes, Defiant, say she's a manipulator and a liar.''



``I've retracted those statements,'' Defiant said.



``And who's to say she hasn't manipulated \emph{you}?  You and Chevalier were arguing for a cleaner, shinier Protectorate, didn't you?  Let's not get off on the wrong foot.  We vet her thoroughly, and if we don't get a consensus that she's an asset to the team, then that's that.''



``What would you suggest, in place of testing and an interview?''



``We do what we're doing with the Cauldron capes, run her by our thinkers,'' Dispatch said.  ``We can get a more concrete assessment of her now, with a field exercise, than by any amount of talking.  If I'm remembering right, a notice went out, didn't it?  A New York group of villains is poaching Wards and Protectorate members?''



``The Adepts,'' Revel said.



``Two birds with one stone,'' Dispatch said.  He looked at the collected captains of the Wards.  ``We want to know how she functions in a team environment, let's put her in the thick of it.  If there's trouble, or if the mission doesn't look good, the rest of us can step in.''



Eyes turned my way.



``You're serious,'' I said.



``As cancer,'' Dispatch told me.



``I don't have any of my stuff, and the costume Dragon gave me isn't my usual.  Besides, you'll be expecting me to follow different rules.''



``You've read the handbook, haven't you?''



I nodded.  \emph{But I haven't completely thought of ways around the restrictions}.  I'd picked the name Weaver based on the idea that I'd be using thread more, but I didn't have any prepared, not here, not yet.



``I'm sure Prism will let you have access to the New York teams' supplies.  Largest cape groups in America, they'll have a little of everything.''



I frowned.  If I said no, it'd be a black mark in my record, and some of these people were obviously not interested in giving me any slack, unless it was to hang myself with.



``Okay,'' I said.



``The Adepts don't kill,'' he said.  ``If there's a problem, it's on you.''



\emph{There should be a rule against saying things like that}, I thought.  I didn't care that he was putting me on the spot, or blaming me for stuff that hadn't happened yet.  He was implying this would be \emph{easy, }practically ensuring this would be anything but.



\sectionbreak



``Adepts,'' Jouster said.  ``I assume everyone's up to date?''



Tecton was walking in front of our group, his tank of a suit giving us enough presence that the crowd parted before us.  ``Don't be a jackass.  You know Skit- Weaver hasn't read the files.  They're in your city, you fill us in.''



``I know the basics,'' I said.  I'd read the file in Tattletale's office.  ``They're wizards, or they pretend to be, like Myrddin.  Led by a time traveller.''



``They're led by Epoch,'' Jouster said, without looking at me.  ``Group is very organized.  Thing you gotta know about New York is it's bigger.  Everything is.  So these guys, there's a lot of them.  They're organized into tiers, and they compete with one another for placement in the tiers, challenging ones in higher tiers, paying a penalty if they fail the challenge.  There's one tier one, two tier twos, three tier threes\ldots all the way down to the tier fives.''



``Fifteen in total,'' I said.



He gave me a hard look, then fell silent.



\emph{Am I not allowed to talk?}



``This city sucks to move around in,'' Hoyden said.  ``Crowds, traffic\ldots how do you \emph{get} anywhere?''



``We have different sub-teams for different roles,'' Jouster said.  ``Lancer group for fast response, those of us who can fly or move over rooftops.  Another group of heavier hitters who're old enough to ride the bikes and licensed to travel the tracks.''



``Tracks?''  Hoyden asked.



``Subways.  You use a computer to help know which tracks you can stay on and when, so you don't get hit by a train.''



``And the ones who aren't old enough, or aren't naturally mobile?''  Tecton asked.



``Foot patrol, or sidekick duty with a Protectorate member,'' Jouster said.



``Loads of fun,'' Hoyden said.



``Am I the only one who \emph{likes} doing the ride-along thing?'' Vantage asked.



``Yes,'' Hoyden said.  ``Definitely.''



Jouster shook his head.  ``It's the job.  They grumble, sure, but it's a few years at most before they get to do the bike thing.''



``I'm guessing you're one of the `lancers','' I said.



Jouster gave me a dirty look, ``What of it?''



``Nothing,'' I said.  ``Just made sense.''



``Flechette was one too,'' he said.  ``She was going to lead the squad when I moved up to the Protectorate, with Shelter taking over as Wards captain.''



``I believe it,'' I said.



``Seem to recall that she'd defected, joined your old team.''



``I don't know anything about that, honestly,'' I said.  ``Only that she had romantic interests towards one of us Undersiders, and-''



``The doll girl,'' Jouster said.



Vantage punched him in the shoulder.



``I didn't know if she was `out', so I didn't want to say,'' I said, feeling lame.



``That's right,'' Vantage said.  ``That's how you're supposed to act.''



The earbud I'd been supplied with buzzed with a woman's voice.  Prism?  ``\emph{They own the building up ahead}.  \emph{Cut the banter }\emph{and focus on the job}.''



A male voice.  ``\emph{Talk us through everything you're doing, Weaver.}''



``Focusing on my bugs,'' I said.



``Tap the earbud twice to start the feed,'' Tecton said.



I tapped it twice, and it beeped faintly.  ``Focusing on my bugs.  I've been collecting them as we moved from the headquarters to this spot, so I have quite a few.''



``\emph{Lethal and venomous bugs aren't allowed, you know that}.''



\emph{Tying my hands}.  It was fine.  ``I didn't plan on using them anyways.  I'm selecting the smallest and most discreet, and sending them out.  It'll take a minute at most, but I'll be able to track their movements.''



``\emph{The Adepts}?''



``Everyone.  I mean, the area's dense, but once I have tabs on the Adepts, I'll have an idea of where the civilians are, too.  It means we can keep them out of danger, and we'll know if anyone runs into the line of fire.''



There was silence on the line in response.  Were they talking about me?  Discussing the particulars?  Hell, was I already breaking rules by violating people's privacy?



I spoke, hoping that I was interrupting them if they were saying something along those lines.  ``I have other bugs on the periphery, drawing out cords of silk.''



``\emph{Show us.  We have a camera in Tecton's suit.}''



Okay, this was getting borderline annoying.  Second guessed every step of the way.



My swarm moved in front of Tecton, swirling.



``\emph{Image, Weaver,}'' it was a different man who spoke.  The fat one\ldots I couldn't remember his name.  ``\emph{We need to do something about appearances, here}.''



``Appearances?''



``\emph{The black, amorphous swarm.  It conveys the wrong ideas.  It's disturbing to any onlookers, and if photos of you using your power on any greater scale made the rounds, it could be fodder for some ugly articles.  You already face an uphill battle, with your reputation as an ex-supervillain.}''



``You're serious,'' I said.  I tapped my ear to shut off the channel, looking at the others, ``Is he serious?''



``Glenn is always serious,'' Clockblocker said.  ``When I first picked my name, Clockblocker, and announced it in front of a live camera so they couldn't retract it, they punished me with intensive lessons with Glenn.''



``They do that any time you screw up on the PR front, like swearing on camera,'' Hoyden said.  ``And in the sessions, he talks to you about your hair, about redesigning your costume\ldots''



``How to talk so you command attention,'' Vantage said, over-enunciating his words.



``How to \emph{hold} yourself,'' Jouster said, straightening his back, squaring his shoulders and raising his chin a touch.



``\emph{We can hear you, you know},'' a woman said through the earbud.  Rime?



``\emph{Maybe we need lessons in decorum,}'' Glenn's voice buzzed in our ears.



Hoyden made a pained expression.  She glanced at Tecton, then ducked low, avoiding the camera, while she walked around to Tecton's back.  She pushed at his shoulder, urging him to turn around.  He rolled his eyes and sighed as he obeyed, and Hoyden prodded him forward until he was standing right in front of a wall.



``I \emph{really} don't know what you expect,'' I said.  ``It's my power.''



``\emph{By all reports, you're a clever girl},'' Glenn said  ``\emph{Surely there's a way to present your power in a less threatening way.}''



I opened my mouth, but the sheer number of protests that came to mind all jumbled together.  I looked at the Wards, trying to see if I was the butt of a joke.



``Lucky, lucky you,'' Clockblocker whispered to me, covering his ear with his hand, ``You get his attention right from the start, and I'm willing to bet he's not going to leave you alone.  It \emph{almost} makes me feel better about the time you crammed those bugs into my mouth and ears.''



Vantage made a face at that.



``So worth the extra shifts I'm pulling this week,'' Clockblocker commented to Jouster.  ``Just to see this.''



``I'm not sure what you want, Glenn,'' I said, after tapping my earbud,  ``I could send my bugs in one at a time.  That's not threatening, right?''



``\emph{Your sarcasm isn't appreciated, Weaver,}'' Defiant informed me.



``I'm willing to play ball,'' I said.  ``I just want to figure out what the he- heck you want, first.  Do you want, like, ladybugs?  There's \emph{color} there, a nice red cloud.  There's only, um, two hundred and twelve ladybugs in my range.  But I could use them.  Or\ldots butterflies?  There's more butterflies than ladybugs.''



I accessed the butterflies in my swarm, drawing them to me.



``Tekky,'' Hoyden said, ``Turn around.  They'll love this.''



``\emph{Tecton},'' he mumbled, stressing the word.  ``I hate `techy', `tech geek' and all those names.  Just like I hate being the camera guy, the guy who the PRT gets to fix the vans when they want to cut work early\ldots''



I drew the butterflies into formation, a stream of them following after one another.



``I just want you to realize that this is what you'd be asking me to-''



``\emph{Yes},'' Glenn said, cutting me off.  ``\emph{Excellent!  They did say you were smart.}''



``You're serious,'' I said.



Clockblocker was laughing silently, his shoulders shaking.



``Serious as cancer,'' Hoyden mimicked her superior.  ``All Glenn cares about is the image, the PR.  Up to you to figure out how to hold yourself like a `lady' while you're dealing with street thugs with guns.''



``\emph{You would know, Hoyden},'' Glenn said.  ``\emph{I'd hoped something would sink in for you, with you having more meetings with me than anyone has in the past year.}''



``\emph{Stick to business, please.  Where did you get all those butterflies, anyways?}'' I think it was Rime, on the comms.



``Rooftop gardens,'' I said.  ``There was a whole block with older buildings and a garden on every roof, while we were heading this way.  Lots of balcony-mounted flower troughs, too.''



``\emph{We'd need to get you a steady supply},'' Glenn said.  ``\emph{I wonder how we arrange that.}''



``They're really going to make me the butterfly girl?'' I asked.



Clockblocker only laughed harder.  I was pretty sure he was faking it, at this point.  He couldn't find it \emph{that} funny.



``\emph{If this is a problem,}'' Defiant said, the earbud's digital sound only compounding the faint digital note of Defiant's voice, ``\emph{We can cancel the job}, \emph{take a few days to discuss}\emph{the tools you need to do the job effectively}.''



The worst of both worlds.  I'd be backing down, they'd probably argue for this as a way to keep me `tame', and I'd look disobedient.



``No,'' I said.  ``You want me to use butterflies, let's do that.''



``For real?'' Hoyden asked.



I nodded.  ``We're picking a fight with the Adepts?''



``\emph{This is only a branch,}'' Prism said, over the comm, ``\emph{They have three primary properties.  They don't hold territory, so the local gangs leave them be.  }\emph{The idea is to discourage them}.  \emph{Fight only so long as you're confident you'll win.  Communicate what's going on, and we'll step in if need be.  With luck, this will be a setback for them, and cause to stop headhunting }from our side\emph{.}''



``Okay,'' I said.  ``Who's in charge?''



``Me,'' Jouster said.



It would be weird to not be the leader, after heading the Undersiders.  ``You okay with me as recon?''



``Suppose you have to be, if you're limiting yourself to butterflies,'' he said.



``I wasn't going to limit myself to recon,'' I said.



``You'll tear them to shreds with butterfly bites,'' Vantage said.  ``Do butterflies bite?''



``They don't have mouthparts that can bite,'' I told him.  ``They have proboscises.''



``So are you like, super smart or something?'' Hoyden asked.



``No,'' I answered her.



``Don't get distracted by the new member,'' Jouster said.



I noted what my bugs were telling me.  ``There's three of them inside.  Two men, one woman.  The men have groupies with them, I think.  In their bedrooms.  There might be more, but they don't have costumes on.''



``They should have numbers on their sleeves.  Roman numerals.''



``I can't really see through the bug's eyes,'' I said.  ``One second\ldots''



I found the woman, sitting on the couch, a laptop on a coffee table in front of her.  The bugs traced her sleeve.



``It's not embroidered, I can't sense anything raised, and the bug's eyes can't make out the letters.  Sorry.''



``Check the surroundings,'' Jouster said.  ``Tools?  The group's practices involve using tools, ritual, rites, chants, and all that crap to try to achieve better control over their abilites.''



``Kind of makes sense,'' I said.  ``Abilities get stronger when you're in a mental state closer to how you were thinking before your trigger event, so-''



``Wait, what?''  Clockblocker cut me off.



``Yeah,'' I said.  ``I triggered while I was in a locker.  I've been thinking, I get just a little stronger when I feel trapped, or when I despair, or when I feel betrayed.  My range extends.''



``It doesn't matter,'' Jouster said.  ``Three of them.  No tools?''



``Sort of a tool.  A rod, short, barely a foot long, and blunt, no barrel or anything.  Carved, I think.''



``Not sure,'' Jouster said.  ``Doesn't ring any bells.''



``Um.  But if you look,'' I pointed.  ``There's birds.  Usually they'll pick off a few bugs that get too close, but they aren't moving.''



``And there's some inside?'' Jouster asked.



``Three\ldots five birds in cages inside the apartment,'' I said.



``Felix Swoop, tier three member of the group,'' Jouster said.  ``Master-blaster hybrid.  Controls birds, but not as much control as you seem to have.  Thing is, he applies fire immunity and pyrokinesis to the birds, programs them with movements.  You said he's distracted?''



I noted Swoop's presence in the bedroom, tried not to pay too much attention to the particulars of what was happening inside.  ``Definitely occupied.''



``Let's move,'' Jouster said.  He began striding across the street.  He raised his voice, ``Back away from the building!''



No reaction from the men in the bedroom or the woman on the sofa.  They couldn't hear it.



I directed my swarm.  Bugs moved through the crowd, and I organized the swarm so it was surrounded by butterflies, masking the core of the `disturbing' black swarm within.



Cheating, maybe, but I'd do what I had to.  The irritating part of this was that I had to \emph{look} at the swarm to make sure everything was in place.  It'd become natural sooner or later, but I really didn't need \emph{more} handicaps.



``\emph{Back away from the building.  You can watch the fight, but watch from the other end of the street},'' I spoke through my swarm.



So \emph{weird}, to be doing this with a veneer of legitimacy.



``\emph{What are you doing, Weaver},'' one of the capes asked me, through the earbud.



``Warning the crowd.  I can mimic my voice by using the sounds my swarm produces, only I'm using mainly butterflies.''



A bit of a fib, but it would fit what Tecton was seeing by way of his camera.



``\emph{Keep us updated on your thought process and strategies.}''



Jouster led the way into the building.



``I'm using the silk cords I prepared earlier to hamper the birds on the balconies,'' I said.  ``There's a pigeon roost above, but I'm covering the door, so hopefully Swoop won't have access to all of those pigeons.  And I've got other bugs surreptitiously gathering in the clothing that Swoop and the other male discarded.  I'm assuming I can use the scarier bugs if the public isn't about to see?''



``\emph{That goes against the spirit of what I was talking about},'' Glenn told me.



``Yeah,'' Hoyden said, from just behind me, ``You should \emph{want} to use butterflies and butterflies only.''



Tecton pushed the door open, splintering the lock and snapping the chain with just the strength of his power armor.



``\emph{Tecton in last,}'' Prism said.  ``We'll want eyes on the scene.''



``I'm the toughest of us,'' Tecton protested.



``Don't flatter yourself,'' Hoyden said, patting his chest as she walked by.



``Two upstairs there, with two more that might be initiates, might be civilians,'' I said, raising my voice a fraction.  I pointed in the direction of the two men.  I moved one hand to point at another point.  ``One woman there.  All two floors up.''



I hung back as the heroes ascended the stairs, and got to see as Tecton placed his hands against the frame of the door.



``Let me know when,'' he said.  ``And brace yourselves.''



We'd gone over the powers in this particular group before we left.  I knew what Tecton and Clockblocker were capable of, obviously.  That left Vantage, Jouster and Hoyden.  I could track them as they broke into the apartment.



Jouster's blaster-striker hybrid power involved his lance, a power that conducted along the usual channels, only the form it took varied.  He speared through the computer, then swung the blunted side of the weapon at the couch.  The woman rolled out of the way, and energy rippled away from the lance, freezing and shredding cushions.



He could choose the effect, making it fairly versatile.  Concussive blasts, fire, ice, lightning, suction and disintegration, among other things.  Trick was that he had to \emph{hit }to deliver the effect\emph{.}



The advantage, conversely, was that he had another power.  With a brief-lived burst of superspeed, he closed the distance to the woman, coming to an abrupt stop just in time to kick her in the midsection.



Clockblocker followed, stepping forward to touch the woman and freeze her.



``\emph{Woman is Paddock},'' Jouster said, through the earbud.



``\emph{Caught her},'' Clockblocker said.



Hoyden and Vantage were already breaking into the other rooms, interrupting the men and women at play.



Vantage had super strength, but his strength and reflexes scaled up as the number of opponents rose, with diminishing returns.  He wasn't especially \emph{durable}, but he packed short-range teleports.  \emph{Very} short-range – a matter of two or three feet, at best.  He teleported to help close the gap to Swoop and slammed one hand into the man's collarbone.  The woman scrambled for cover.



``\emph{Anyone want to break the wishbone?}'' he quipped.



The other man raised a hand at Hoyden, and she stopped in her tracks.  He almost leisurely stood, taking the hand of the girl beside him, then reached down to collect his robe, and recoiled in horror at the bugs that festooned it.  He couldn't get to the rod, whatever it was supposed to do.



``Heads up, Hoyden's ensorcelled or something,'' I said, communicating through the earbuds.



``Nuh uh,'' I could hear her speak through the earbud.  She caught the cape from behind, then hurled him through the doorway, at Clockblocker.  He stepped on the man's bare back, and the man was frozen.



``Cape two captured,'' Clockblocker said.



Hoyden was one of the capes with a mess of powers.  Things she hit exploded, things that hit \emph{her} suffered a retaliatory explosion.  She was stronger, more durable, and to top it all off, she had a peculiar resistance to damage and powers that improved as she got further from her target.



Between them, they each had the ability to apply their abilities in devastating ways.  They were team captains for a reason.



Wait, was this okay?  I'd barely done anything.  I was used to hanging back, supporting my allies, and delivering decisive strikes where necessary, but I was supposed to be \emph{proving} something.  Would I be able to say I'd achieved anything definitive?



Was that \emph{intentional}?



I hurried up the stairs in double time.  I reached the door frame, and I got a \emph{look} from Jouster.



Definitely intentional.  He'd had his team bulldoze through the capes, leaving nothing for me.  I'd provided recon, but would that be enough?



``Securing the bystanders,'' Clockblocker said, from across the room.  He approached one of the women, and she made a squeak of alarm as she jumped back from his reaching hand.  ``Shhh, it's okay.  Doesn't hurt.  If you've done nothing wrong, there's nothing to worry about.  You'll wake up in a few minutes, visit the police, and then go home.''



She glanced at Jouster, as if looking for confirmation, and Clockblocker touched her, freezing her.



The other woman was pulling on pants, the kind of skinny jeans you pulled up inch by excruciating inch, if you were lucky enough to have actual \emph{hips}.  She still wore a black bra, and way too much eye shadow.



``Last one,'' Clockblocker said.  ``You can call in the PRT vans.''



She buttoned up her jeans, then ran her thumb along the chain that ran from her belt loop to her pocket.



``Wait,'' I said.  The chain- there were charms on it.  ``Those charms.''



``My \emph{embellishment},'' she said.



``Shit!'' Jouster said.  ``Clock!''



Clockblocker lunged, but she leaped back.  Landing on his hands and knees, Clockblocker reached out, firing the fingertips of his glove at her, each trailing cords that extended to his gauntlet.  Two of the cords looped around her limbs as they made contact.  Thick, I noted.  Not fishing lines that might cut when they were frozen in time.



He froze them, then freed his hand from the glove.  She was immobilized.



It wasn't enough.



``It's Standstill,'' Jouster said.  He broke into a run, charging her with his lance held ready.



``Thirteenth Hour, now,'' she retorted.  Her eyes flared with light, and I felt my body jolt.



``\emph{Tecton}!'' I spoke through my bugs.



My heartbeat slowed to a glacial pace, my breathing slowing.  My outstretched hand started drifting down, the strength to hold it up slowly leaving my body.



Thirteenth Hour collapsed, going limp in the midst of Clockblocker's suspended wires.  Jouster, mid-stride, did much the same.



My \emph{thoughts} were slowing down, volition gone.  The others were the same.  My sense of time\ldots  I was reminded of a dream I'd had, of being put under a spell by Coil.  \emph{Scopolamine}.



Clockblocker's power wore off the various Adepts, one by one.  They composed themselves, dressing.



Swoop dialed a number on his phone, approached the sleeping Thirteenth Hour while holding it to his ear.  He lifted her chin and kissed her, staying beside her to catch her as the cords were released.



``Spot of trouble,'' he said, with a faint accent.  Australian?  British?  ``Wouldn't mind one of the top tiers.  They'll have reinforcements.''



My eyelids drifted closed.  I didn't have the will to raise them.



But I could follow my bugs as they stirred, converging, moving as if with a mind of their own.



Following my unconscious directives?



The bugs went on the offensive, biting, stinging.



\emph{No}.  It wasn't even a coherent thought.  I'd get in trouble.



``\emph{No},'' the bugs whispered, their droning forming crude words.



Swoop and the others startled at that.  I could sense their movements through the accumulated bugs.  He made a hand gesture, murmured a phrase, and birds took flight from the cages around the apartment.  After a moment, they ignited, winging their way through the thickest areas of the swarm.



The others would be arriving soon.  I had to do \emph{something}.



That urgency, more than anything, seemed to translate into an order for my swarm.  They began moving, bearing silk threads.



\emph{That}, I was okay with.



The binding they performed was carried out as if from some deep-seated, creative part of me, the part of me that would doodle absentmindedly in the margins of my notebook when I was tired in class.  Instead of aimless doodles, however, it was cords and lines of silk extending from table legs to feet, from wrists to earrings and between the loops of shoelaces, and it was all accompanied by the butterflies that I was still maintaining in formation.



Swoop's improvised phoenixes couldn't get close enough to burn those things without burning the individuals in question.



The other Adepts were arriving.  My sense of time, still, was obscured.  Where were the Protectorate capes?



How long would we be stunned like this?



Swoop, one hand pressed to his collarbone, moved his other arm to allow a flaming pigeon to rest on one hand, then winced in pain as he wound up nearly yanking an earring out.  ``Curses!'



He really said things like `curses'.



I did \emph{not} want to lose to these guys.



The bugs were still moving, aimless, without my active direction, but they were using the silk cords.



\emph{Butterflies}, I thought.



The butterflies I'd been prepared to use moved into the formations I'd instructed, joining and complementing the swarms of bugs that were weaving webs of silk over and around the four Adepts, including the sleeping Thirteenth Hour.  I could sense her breathing.



How to break the spell?



\emph{Tecton}.



He was under the effects.  I could tell, by how his arms had drooped from where he had them on the door frame.



If this was simply a kind of hypnosis\ldots



I called bugs to me, directed them to gather on my face.



Not enough\ldots they couldn't get through my mask.



Without me asking it to, a cockroach started chewing through the fabric.  The fabric that wasn't nearly as strong as spider silk.



The female Adept that Jouster and Clockblocker had attacked as they entered the apartment made her way toward the kitchen, stumbled as a silk cord around her knees failed to give her enough give.



``Annoying,'' she said.



``Admirable, almost,'' Swoop commented.  ``This is the sort of thing we hope to \emph{train}, and she's already a fair hand at it, isn't she?''



``Whatever,'' the woman said.  She drew a kitchen knife from a wooden block on the counter, then began cutting the most obvious threads.



Seconds, minutes, hours passed.  I couldn't say for sure.  There was fighting outside.  Capes fighting capes.  I couldn't focus my attention on it.



With the hole in my mask now large enough, the cockroach wormed his way in.



Two ways this could go, I realized, as it dawned on me what I was doing.  What my \emph{passenger} was doing?  Either this worked, or it would fail disastrously, and they'd be distracted, at the very least.



The cockroach reached the back of my throat.  I gagged and coughed.



And that disruption was enough to shake off Thirteenth Hour's influence.  My thoughts began to coalesce into something more coherent.



Still coughing, fighting the urge to throw up into my mask, I directed bugs into the eye holes of Tecton's mask, down to his mouth, to do much the same.



``No,'' the cape with the rod said.



\emph{Another} mind-affecting power.  I could see my spiders getting larger as they crawled, the apartment getting smaller, I felt vertigo\ldots



Tecton reached out to the doorframe and made the building shudder with enough force that everyone stumbled.



Everyone woke, Thirteenth Hour included.  The hallucinations stopped.



``Again!'' Swoop shouted.



Thirteenth Hour's eyes glowed, her power flaring\ldots



But I was ready.  A cockroach mobilized to set off my gag reflex a second time, and I was alert before the effect had even sunken in.



\emph{So gross}.



Vantage and Jouster wore masks that covered their mouths.  It'd take a second to get into Tecton's, and I didn't want him to unwittingly wake Thirteenth Hour again\ldots



I woke Hoyden instead.



I wasn't making friends or allies here, I suspected.



Hoyden strode forward, coughing and wiping at her mouth.  A flaming bird soared at her face.  In the instant it made contact, it detonated in a ball of flame and unburned feathers.  She was thrown backwards.



Another homed in on me.  I wasn't durable, like Hoyden.  I shielded my face with my arms.



The armor protected me, the cloth didn't.  I could feel it as though something scraped against my flesh, felt the hot prickle that promised future pain.  A burn.



``Stop,'' the cape with the hallucination power said.  He made a sign with his hands, extending his rod at me.



Again, I felt the sensation of things distorting.



I was free of Thirteenth Hour's power, though, and my bugs were winding silk around his arm and face.  He clawed at it, to little effect, and the more butterflies that settled on his face, the less effective he seemed to get.



Hoyden had returned, and endured a barrage of more flaming birds.  The larger birds weren't obliterated as they exploded, and circled around to strike her again.  I ducked below one I could sense only by the bugs it burned along its path, then backed away.



The one with the knife.  I tied some silk around the knife handle, connecting to the silk between Swoop's leg and the table.



She tried to bring the knife down to cut something, and the cord went taut, pulling it from her hand.  She tried to bend over to pick it up, and the thread between her throat and the light fixture pulled taut.



What was her power, even?



I wasn't interested in finding out.  I navigated the threads by using the bugs to track their placement.  The armor Dragon had fashioned didn't have compartments inside the armor panel at the back, but I had a taser dangling from my belt.  Before she could figure out a way to break a thread, arm herself or use her power, I jabbed her with the taser.



She fell, momentarily suspended by the threads.  I had the bugs near the light fixture manually break the thread before she strangled.



That left Swoop and Mr. Hallucination, who was apparently suffering for not having removed more threads from himself earlier.  He swatted at the butterflies.



I reached Jouster, shaking him.  When he didn't rouse, I shook him harder.



Nothing.  Not \emph{jarring} enough.



I kicked his leg out from under him, and he sprawled.



``Fuck you,'' he mumbled, as he began to climb to his feet.



``Wake up Clockblocker and Vantage,'' I said.



``You don't give me orders,'' he said.  He approached Swoop.  The man smacked Hoyden with one more bird, whirling around to face Jouster, and then got slammed in the chest with the fattest part of the lance.  The third tier Adept flew into a wall and went limp.



Jouster wanted to clean up?  Fine.  I tazed the hallucination guy, then hurried to Clockblocker's side.  When shaking him didn't rouse him, I raised his head from the floor and then smacked it down hard enough to startle him.



``Jerk,'' he mumbled.



Jouster had poked Vantage awake.



``Our reinforcements are fighting their reinforcements,'' I said.



``Good to know.  We get Tecton and back them up.''



``You kicked their asses with butterflies,'' Clockblocker said, as we made our way to the stairs.



``I cheated.  The butterflies are superficial, decorative.''



``No, no, no,'' he said.  ``If anyone asks, you kicked their asses with butterflies.''



\sectionbreak



Defiant and I walked back through the corridor of double-layered chain-link fence.  There was a long pause as the gates opened.



``You may have won over some of the ones with doubts, but Rime was grumbling about your attitude, and I suspected she was on your side to start with.''



``My attitude?''



``I don't know.  Something to ask her, when the time comes.''



I sighed.



``Your arms?''



``Hurt,'' I said.  I extended my arms, prodding at the bandage on my forearms.  ``Nothing serious.  Will probably peel like a motherfucker.''



``Language,'' he said, as we entered the hub.



The warden was there, waiting for us.



``You got injured.''



``In the line of duty,'' Defiant said.  ``\emph{Permitted} duty.''



``I told you to keep her out of trouble.''



``Wasn't my choice,'' Defiant said.  ``I can give you my superior's number if you'd like.''



``I \emph{would} like.  Taylor Hebert?  On the issue with the bug population of my facility, I feel it would be a very bad idea to provide you with a caustic substance to give your bugs, given what your file says you achieved with capsaicin.  I had a bug zapper purchased, and you should be able to access it with each and every one of your tiny soldiers.  I expect to see it used, understand?''



I nodded.



``Go change.  I'll have a guard waiting here to escort you to your cell.''



``Okay,'' I said.



I changed back into a fresh prison tunic and pants, leaving my shoes behind.  It pained me to leave everything behind, but I did.  The female guard patted me down when I'd emerged and handed the bundle of clothes to the guard at the hub's office, then led me to my cell.



I was cognizant of my fellow prisoners, who watched me.  Prisoners who, I had little doubt, saw my injury as a sign of weakness, a reason to descend on me like wolves with wounded prey.



Being out among the Wards had shaken me, on a level.  I still needed to find out how to fight like a \emph{Ward}.  A more effective Ward than the ones I'd encountered in the past, ideally.  I needed to adjust my tactics, the very way I \emph{thought}.  To build a measure of self-confidence that wasn't borne by fear and intimidation.



I settled down on the bunk with my book.



I shifted restlessly.  I still had trace amounts of adrenaline in my system.  The rush of a fight.  My arms hurt, too, despite the over-the-counter painkillers I'd tossed back.  A second degree burn, and like so many other injuries of the hands and arms, they seemed as though they had been strategically placed where they'd be most irritating and debilitating.



\emph{Tonight is going to suck,} I thought.  How was I supposed to get comfortable like this?



My bugs found the bug zapper, and I began systematically eliminating every cockroach, louse, fly and ant in the building.



The spiders, I kept on hand, directing them to the burned corpses.  They could breed, in time, and I could put them somewhere where they wouldn't encounter any people.



Breaking the rules, maybe, but it was something to occupy my thoughts.  It made me feel just a little safer, a little more like myself.





