





Every part of the Las Vegas team's reaction to our arrival screamed dissatisfaction.  Folded arms, the way none of them would meet our eyes, the very way they were positioned, so they were just enough in our way to make it clear they didn't agree with what was going on, but not so close as to be \emph{with} us.



Except it wasn't \emph{me} that was the problem, this time.



Satyrical, Satyr for short, wore a helmet sculpted to look like a goat's head, the mouth in a perpetual smile.  On a good day, I imagined his eyes were bright with mischief, his shaped eyebrows quirked behind the large eye-holes of the helmet.  This wasn't a good day.  There were circles under his eyes, and he glowered.  With the smile on his helmet, it made him look\ldots I didn't want to say deranged, but it was the word that sprung to mind.



His bare chest was muscular, waxed hairless, the belt and leggings of his costume slung low enough that I could see the lines of his lower stomach that pointed to his\ldots yeah.  It was admittedly distracting.  It was \emph{meant} to be distracting.



Nix, Blowout, Leonid and Floret joined Satyrical in their anger.  Heroes in more flamboyant and colorful costumes than normal, their moods a contrast in how dark they were.  Spur and Ravine seemed more lost than angry, but the way they retreated into their group as we passed told me that they would side with their team over us.



If there was something to be said, words of encouragement or apology, nobody I was with seemed ready or able to come up with them.



We approached the elevator and made our way down, and none of the local heroes joined us.



``Thoughts?'' Vantage asked me.



``For a city like Las Vegas, I'm surprised the building is so\ldots'' I trailed off.



``Dull?  Like a giant tombstone?''



``No windows,'' I said.  ``Just the front door, walls all around it, no decoration except for the PRT logo on the face of the building, no lights except for spotlights.''



``Stands out,'' Vantage said.  ``There's contrast.''



``And it's required.  Vegas is one of the worst cities for sheer number of villains,'' Rime said.  Her entire demeanor was rigid, which maybe fit in a way with her ice powers.  ``Vegas employs a group of unsponsored thinkers and tinkers to monitor the venues, much like the PRT does with the economy, ensuring that everything is above-board, that everything is being conducted fairly and that the numbers add up.  Vegas changed as a result, developed a different cape dynamic.  In Los Angeles or New York, it's the people who can blow down buildings that are seen as true `heavy hitters'.  Here, they're trying to game the system, and the heroes are trying to game \emph{them}.  In Vegas, it's thinkers, tinkers and strangers who rule the underworld.''



``A different sort of cops and robbers,'' I said.



``Cops and robbers?''  Vantage asked.



``A way my teammate once explained it to me.  The, for lack of a better word, \emph{healthy} way for heroes and villains to be, is for all of this to be a game of sorts.  Trading blows, counting coup, but ultimately leaving the other side without any permanent damage.''



``Counting coup?'' Leister asked.  He was the sole subordinate that Vantage had brought along.  Rime, by contrast, had brought Usher and Arbiter from her team.  Prefab from San Diego had shown up as well.



I explained, ``The term came from the Native Americans' style of warfare.  In a fight, one person makes a risky, successful play against the other side showing their prowess.  They gain reputation, the other side loses some.  All it is, though, is a game.  A way to train and make sure you're up to snuff against the \emph{real} threats without losing anything.''



``Except,'' Rime said, ``Things escalate.  One side loses too many times in a row, they push things too far.  And there's always collateral damage.  I notice civilians don't factor into that explanation.''



``I'm not saying I agree with it a hundred percent,'' I said.  ``I didn't, even from the beginning.  But it sounds like what you're describing.''



Rime shook her head.  ``No.  The strip is dying.  Every successful job the villains pull causes catastrophic damage, sees venues shutting down.  More villains arrive, hearing of the last group's success, or because there's \emph{room} for them, and they settle in the more desolate areas.  The problem feeds itself, gets worse.  This building is a fortress and a prison because that's what the city needs, that's how bad things have gotten.''



``And the heroes?''



``Flamboyant, as brilliant and attention-grabbing in the open as the villains are discreet and hidden in plain sight.  The Vegas team is largely made up of strategists, charlatans and borderline scoundrels.  Individuals who can foil cheats and frauds, or throw a wrench in the works of the local masterminds, who \emph{think} like they do.  Which is why \emph{this} is such a problem.''



The last sentence had a note of finality to it.  I decided not to push my luck with further questions.



We made our way out into the corridor with the cells.  It was deeper, more developed than Brockton Bay's.  There were two tiers, with one set of cells above the other.



Rime moved her phone next to a television screen, then tapped it.  There was a pause as a row of black squares with white outlines gradually lit up.  She leaned forward a little, her hand resting against the wall beside the television.



The screen came alive.  I saw a man in a cape uniform within, without a mask.  He had albinism, to the point that the velvet purple of his costume overwhelmed the little of his skin that was showing.  The irises of his eyes were a dark pink.



``Pretender,'' Rime said.  Her voice had a harder note than before.  ``What have you done?''



``Don't place all of the blame on me.  You forced my hand.''



``No,'' she said, ``There had to be another way.  You could have admitted--''



``A death sentence,'' he said.  ``You're an upper-echelon cape now, and you have the clearance.  You know about \emph{her}.  The bogeyman that comes after anyone who tries to release information \emph{they} want to keep secret.''



I glanced at Vantage, who only shrugged.



``We could have protected you,'' Rime said.



Pretender only chuckled.  ``No.  No you couldn't.  I'm dead anyways, one way or another.  I surrender, it's the end of my career, and that's all I have.  I talk, I die.  This was the best option.''



The hand that Rime was using to lean against the wall clenched into a fist.  Her voice was tight as she asked, ``Killing a government thinker was the best option?''



``Yes.''



Rime straightened, but it was more of a defeated gesture than anything, her hand dropping from the wall.  ``You were one of the good ones, Pretender.''



``Still am,'' he said.  He crossed the length of his cell, sitting on the corner of the bed.  ``I'd explain, but it would only get us all killed.''



``We're going to have to take you to a more secure facility,'' Rime said.



``Well, I didn't expect you'd let me go.  Do what you have to.  I made a deal with the devil, you caught me, for better or worse,'' Pretender said.  In a quieter voice, he said, ``About time I pay the price.''



Rime turned off the television.  She looked at Arbiter.



``My riot sense was going off like crazy as he talked,'' Arbiter said.  ``There's something at work here.''



``Describe it.''



Arbiter touched her middle fingers and thumbs together, forming a circle, ``Orange.''



She moved her hands further apart, ``Red.''



Then further apart again, until the implied `circle' was as big as a large pizza.  ``Yellow.''



``That bad?''  Rime asked.



``Bad.''



``Then we move now,'' Rime said.  She raised her hand to her ear.  ``Dragon?  Cancel your errands.  We're in for some trouble, almost guaranteed, and I'm thinking we want to clear out before it descends.''



There was a short pause.



The digital voice of Dragon's A.I., the same one I'd heard through her drones and the armbands, informed us, ``\emph{Kulshedra model en route to Las Vegas Protectorate Headquarters.  ETA two minutes.  }\emph{Tiamat }\emph{to join in t-minus eight minutes}.''



``Okay,'' Rime said.  ``It'll be here before we're on the roof.  Let's get Pretender packed up.  Standard stranger protocols in effect.  Usher and Arbiter, you handle it.  Everyone else with me.''



Once we were all in the elevator, I figured I was clear to ask without sounding too much like a newbie.  ``What was Arbiter talking about?  Riot sense?''



Rime explained.  ``She's a social thinker, in addition to her minor blaster and shaker powers.  Her danger sense is mild at best, not something she can react to immediately, but it makes her aware of associated individuals and the threat \emph{they} pose.  She wouldn't be able to see much from Pretender alone, but she knows that there's a moderate to high danger posed by those closest to him--''



``His team, probably,'' Prefab said.



``She's predicting a massive risk from people who have an intimate but less \emph{immediate} association or those who have a recent but less familiar association with him\ldots''



``Old teammates or family that he doesn't see regularly,'' Prefab said, ``Or people he's hired for help that he isn't as familiar with.''



Rime finished, ``\ldotsAnd a moderate risk from people or things on the periphery of his real-life social network.''



``The bogeyman?'' I asked.



Rime didn't answer.  Instead, she looked at the digital display above the door of the elevator.  ``Prefab, look after our Wards.  I'm going to have words with Satyr.  See if we can't work out what the angle is.  Wait on the roof for our ride.''



``Stranger protocols mean you don't go anywhere alone,'' Prefab said.



``Of course.  I'm thinking\ldots  Vantage,'' she said, beckoning.



Vantage nodded, stepping forward.



The elevator doors opened for Rime to exit, then shut.  The three of us continued up to the roof.  Prefab was large, and his armor made him look larger, with shoulderpads that looked like the tower-tops of a castle, each probably weighing twice as much as my entire outfit, equipment included.  He carried a heavy cannon, obviously tinker made.



Leister was a teenager in lightweight silver armor with the edges molded into wave-like forms.  Beneath the armor was blue cloth with a similar wave-like design embroidered on it.  He held a trident, as ornate as his armor.  As lightweight and sprightly as Prefab was a veritable tank.



``This bogeyman--'' Leister started.



``Based on what we know,'' Prefab said, ``Arbiter giving us a yellow that possibly includes \emph{her} is more worrying than a red alert involving just about anyone else.''



``You don't know anything about her?''



``We mainly see her censoring information,'' Prefab said.  ``Silencing and disappearing people who are talking about sensitive stuff, and doing the same with everyone they talked to.  Only details are slipping through the net, now.  About Cauldron, about Alexandria, the formulas.''



``Too much for one person to handle?'' I suggested.



``Speculation from the top is they've probably stopped caring,'' Prefab said.  ``Thinkers believe she's \emph{letting} things leak, because it doesn't make sense that they'd keep things this tight and then slip up like they have been.''



``What's her classification?''



``Thinker.  Don't worry about the number.  Just run.''



I frowned.



``Exactly how many capes are like that?'' Leister asked.



``A handful.  Enough.''



``I'm beginning to feel like I'm out of my depth,'' Leister said.



``You get used to that,'' I said.  ``With the sheer luck involved in powers and the crap we wind up facing on a daily or weekly basis, it's only a matter of time before you wind up going up against someone you don't have a chance against.''



``Yeah, but Fab's talking--''



``\emph{Pre}fab,'' Prefab growled.



``Sorry.  I mean, Prefab was talking about opponents we couldn't \emph{hope} to fight, and I've only had two real fights so far.  One of them wasn't even a real fight.''



``You're new?'' I asked, raising my eyebrows.



``I've only been a Ward for a month.''



Only two fights in a month.  I felt a pang of envy.



``Let's hope there isn't a fight today,'' Prefab said.  ``But let's be ready if there is one\emph{.}''



We ascended to the rooftop.  Dragon's suit had already landed.  A bulky craft, twice the size of a helicopter, with what looked to be a cargo bay.  Letters stenciled on the edge of the wing read `Kulshedra v0.895'.



Inside, in boxes, there were butterflies.  Innumerable varieties.  Sadly, quite a few had died due to a lack of food or being crushed under the weight of the others.  The idea was clear.  The PRT wanted me to change how I operated.  Dragon, at least, was willing to give me the means.



It was still stupid.  Ridiculous.



The back of the craft opened, giving me access to the hatches.  I stepped up onto the ramp and found the buttons to open the boxes.



``Go, my pretties,'' I said, monotone.  ``Go, seek out my enemies and smother them.''



They took off, moving in colorful formations, organized by type, drawing fractal shapes in the air as they spread out.



I stepped down off the ramp to see Leister staring at me.



``I know you were joking,'' Prefab said, ``But no smothering.''



``No smothering,'' I said, sighing.  I looked up.  The sky was darkening.  ``If there's a fight, it's going to be at night.  It'd be pretty stupid to use butterflies at night, when half of my tricks are \emph{subtle}.''



``You'd have to ask Rime.''



\emph{Was I supposed to use non-butterflies to scout for trouble?}



I considered asking, but I was suspicious I already knew the answer.



Best not to ask, and beg for forgiveness later.



Insects and flies moved out over the surrounding cityscape.  There were too many buildings here, too many that were sealed off, but I could check rooftops and balconies, and I could investigate the ground.  Tens of thousands of people, all in all.



``Sniper rifle,'' I said, in the same instant the thought came together.



``Wha?'' Leister asked, incoherent and confused.



Prefab's head snapped my way.  ``You sure?''



``I'd point,'' I said, ``But he'd notice.  Our masks and helmets cover our faces, or I'd be worried about lip-reading.''



``Don't panic, don't give away that you're afraid.  Into the craft.  Go,'' Prefab said.



I nodded, wishing I had my real costume, though I knew it might not be tough enough to withstand a bullet from a \emph{sniper} rifle.



Prefab was the last to step inside, slowing down as he approached the ramp.  I could see light glittering around the edges of the roof, growing more intense over the course of seconds.  Ten, fifteen seconds passed, until there was more of the light than there were spaces in between.  The light was most intense near the edges.



In a clap of thunder, a rush of wind and a flare of\ldots anti-sparks, crenellated walls appeared, extending fifteen feet up from the lip of the roof's edge.  The sparks, such as they were, were black at their core, surrounded by shadow.  They spun in the air before drifting to the ground, where they flickered out of existence.



``Does that block his line of sight?  I can make them taller,'' Prefab said.



``I don't think he has the right angle to shoot over the wall,'' I said.



``No weapons?  Costume?''



I used my subtler bugs, but he was already packing away the rifle in record time, then swiftly moving away from the roof's edge.  He brushed away my bugs as they converged, kicked a hatch open with his foot, then climbed inside with a speed that almost made me think he'd fallen.  Only the fact that the hatch closed firmly after him convinced me otherwise.



The only way he'd have evaded the swarm like that was if he'd known what I was doing.



``No costume,'' I said.  ``He brushed away the bugs before I could get anything substantial, but I think\ldots glasses?  And a dress shirt.  I think he noticed what my bugs are doing.  That's rare.''



``We've got trouble,'' Prefab said.  I realized he was using his phone.  ``Sniper on a rooftop nearby.  Possible Thinker.  Barricades should make for safe elevator exit.''



``\emph{We're on our way up},'' Rime said, through the speaker.  ``\emph{Four capes and the containment box.  Hold position, play safe.  If Pretender arranged a jailbreak, he won't have just one person working under him.  Arriving in eight, seven, six, five, four, three, two, one\ldots}''



The elevators opened.  Rime, Arbiter, Vantage and Usher made their way out, wheeling a box along with them.



``Password?'' Prefab asked.



``Twenty-three-aleph-pater-newfoundland-washington-vikare,'' Rime said.  ``Arbiter's group is already confirmed, they haven't left my sight.  First half of your first password?''



``Eight-nine-three-scion,'' he responded.  ``And the other two are clear.''



``Good.  Let's move. A hand?''



Prefab gave Rime a hand in moving the box.  It couldn't have been comfortable: four feet by six feet by four feet.  Enough to stand in, but not enough to lie down.  The thing had four wheels, and was dense enough that it took some muscle to get it up the ramp.  I would have joined in, if I didn't fear I would get in the way more than I'd help.  I wasn't the strongest person around.  Fit, yes, but not \emph{strong}.



Instead, I focused on bringing my butterflies back.  I couldn't get them all back in time, but a loss of a hundred or so wasn't a tragedy.



A loss of \emph{all} of the butterflies wouldn't be a tragedy.  I'd feel bad, if only because of the trouble Dragon likely went through in acquiring them, but yeah.



\emph{Gosh, if they all just happened to die or get left behind, maybe I'd have to use something else.  Tragic}.



They finally managed to settle the box at the center of the cargo bay, pulling a switch to close clasps at the base of it, lowering a solid metal pillar from the roof to the top of the box.



I doubted it would budge if someone crashed a bus into it.



I called back some of the butterflies closest to me, keeping others around the building with the sniper.  He hadn't set up again.



``I'm worried about that sniper,'' I said.  ``If he was coming after us, why is he giving up so easily?  If he \emph{wasn't} coming after us, who was he after?  A civilian?''



``Identify the building as we get airborne.''



``Through a window?'' I asked, looking forward, to the `head' of the craft, that looked out onto the city.



``Bulletproof glass or no, let's stay away from the windows for now,'' Rime said.  ``Kulshedra, show Weaver what your cameras see.''



Monitors changed from red text on a black background to high-resolution images of the surrounding walls and rooftop, a different image for each one.



A second later, the ramp closed, and we took to the air, the craft vibrating softly.



I studied the monitors, watching, getting a sense of the surroundings and of which buildings corresponded with what I was looking at.



``Kulshedra,'' I said, pretty sure I was mangling the name, ``The leftmost monitor on your left side.  Zoom in, a little up and left.  There.  Building to the left of the one in the dead center.''



I tapped the screen as the ship highlighted the building in question.



``Good job, Weaver,'' Rime said, peering at the monitor.



``Was on the roof, moved below through hatch when I used my bugs.  Hasn't left the building,'' I said.



Rime touched her earbud.  ``Vegas teams, be advised, armed individual in a building at\ldots 125 West Sahara.''



``It's port,'' Leister murmured to me.



``Huh?''



``You said `left side of the ship.  It's port.''



``Isn't that boats?'' I asked.



``Can be aircraft.''



``Best leave it,'' Vantage said.  ``Leister's a little stubborn.''



``So am I,'' I said.



``Maybe `tenacious' is the word you want,'' Vantage offered.  ``There aren't a lot of people who get knocked out and still manage to win a fight.''



``Are you \emph{all} this pedantic?''  I asked.



Vantage only laughed, though I saw Rime glancing at me, and she didn't look pleased.



``Alexandria was always hard on us,'' Arbiter said.  Her voice had a strange tone to it, oddly melodic, ``Getting us to focus on grades, extracurricular stuff, on top of what we did as a part of the team.''



``We were challenged to be better than the other teams in everything, academics included,'' Vantage said.  ``But we were the only team with a leader who cared about it.''



``Except the capes in Fresno,'' Arbiter said.  ``I was still a Ward, then.''



Vantage smiled, ``Oh yeah.  The bastards in Fresno.  They caught on, probably because we were complaining so much.  Small team, but they started studying like crazy, \emph{just} so we'd be in second place, academically.  Didn't matter \emph{why} we were second, Alexandria was still annoyed at us.''



``All those sermons on being top-notch, on \emph{acting} like the people we wanted to be, and\ldots she turned out to be a monster,'' Arbiter said.



``A monster slain by Weaver, here,'' Usher spoke.



All at once, I felt \emph{very} on the spot.  Each of the capes here, Rime and Prefab excluded, had worked with Alexandria in some capacity.  Except Rime and Prefab were team leaders, and Defiant had commented on how every cape in a position of power had some experience working under the Triumvirate, so even they knew her to some extent.



``Weaver did what had to be done,'' Rime said.  ``Not pretty, not kind, but sometimes you have to use a knife to cut out a cancer.''



All eyes were on me.  Nobody was speaking.



``I asked you to come along on this job for a reason, Weaver,'' Rime said.  ``I've read the incident reports that involved your interactions with the PRT and the groups under the PRT's umbrella.  The bank robbery, the fundraiser, the theft of the database with the Shadow Stalker kidnapping, and your ultimate surrender, a little over a week ago.''



I nodded, not sure where she was going, not wanting to interrupt.



``On the latter two occasions, you and your team perverted the natural course of justice.  You pretended to be defeated by Shadow Stalker in order to ambush the Wards, and you later surrendered, only to get off rather lightly for your crimes.''



``I think I follow,'' I said.  I glanced at the others, but they were all busy trying not to look like they were listening to our conversation.



Rime nodded, ``It's about--''



The ship lurched, and Rime broke off mid-sentence to catch herself before she fell to the floor.  Usher fell and nearly slid across the floor, but Vantage caught him.



``Kulshedra!'' Rime shouted, ``Report!''



``\emph{Incoming fire.  Taking evasive maneuvers}.''



``The sniper,'' I said.



``\emph{Not likely,}'' the ship reported.  ``\emph{Unless the sniper is capable of moving great distances, he is approximately point seven three five miles away.  The missile came from a perpendicular direction.}''



``\emph{Missile?}'' Leister asked, sounding very alarmed.



``\emph{Projectile},'' the ship corrected.  ``\emph{Humanoid in shape}.''



I saw Leister relax a fraction at that, which I found oddly charming.  He was \emph{relieved} it was just a person.  Experience told me that small-to-medium sized explosives were \emph{less} daunting than the prospect of fighting an unknown parahuman.



``Let me out, Kulshedra,'' Rime said, ``Before they attack again.  Follow my orders on comm channel two.''



The back of the ship cracked open, and wind rushed into the cabin.  Several of my butterflies were torn free of their roosts.



``Prefab's in charge,'' Rime said.



``Got it,'' Prefab answered.



``Usher?'' Rime asked.  ``Hit me.''



Usher didn't respond, still struggling a bit with his precarious position, holding on to Vantage's hand.  He did close his eyes, and Rime began to glow, a sheen radiating over her hair, skin and costume.



With that, she was gone, pushing her way out of her seat, leaping and taking flight, flying out of the open hatch.



An instant later, the ship swayed again.  Prefab used his power to create a short half-dome over Usher.  The back hatch closed, and Usher was finally able to relax, with solid ground and something to hold on to.



``\emph{Projectile was rotating rapidly, along both horizontal and vertical axes.  Rendering composite image from video footage.}''



The monitors showed a gray expanse, but it began to rapidly take shape in what was first a distorted sphere, then a crude face, and finally a face complete with details.



Arbiter, Vantage, Leister and Prefab all groaned in unison.  I suspected Usher might have joined in if he had a better angle..



``Fuck you, Pretender,'' Vantage muttered.  ``Fuck you.  You had to hire the worst mercenaries possible, didn't you?  You \emph{asshole}.''



I looked at the image.  Not a face I \emph{knew}, but one I recognized from TV, from the internet, and one very brief encounter.



``That's B--''



The ship swerved, but it didn't manage to avoid the hit this time around.  This time, the shifting center of gravity was compounded by a sudden impact, heavy enough to cave in the front of the craft.  Each and every one of us were thrown out of our seats.



From there, things went south quickly.  No longer flightworthy, the ship struggled to maintain altitude.  Bugs that had collected on the outside of the ship made me aware of how the jets that had been driving the craft forward were now angling towards the ground.  They worked double time to keep the Kulshedra from spinning as it fell and to give downward thrust to counteract the pull of gravity.



Rime's power froze the Kulshedra in mid-descent, catching it between two buildings, suspended in the midst of a bridge of ice.



The projectile struck us again, from directly above.  The ice to our left, our \emph{port side}, shattered.



``Seatbelts on!''  Prefab bellowed.  ``Hold on tight if you can't get to one!  Deep breath, don't tense with the impact!''



I climbed up to a point where there were benches, and belted myself in.  One over each shoulder, one over my lap.  The headrest- it wasn't there.  There was only metal.  My butterflies found the real headrest above me.  I reached up and found the clasps to lower the softer bundle until it sat at the right height to cushion any impacts.



The ice on our starboard side cracked, an agonizing, gradual break.  My heart leaped into my chest as we plunged towards the street below.



The Kulshedra hit ground, and the impact was so heavy my thoughts were jarred out of my head.  For long seconds, I couldn't think, but could only \emph{experience}, could only feel every part of my body hurt, aches and pains I didn't know I had magnified by the jolt.



It was a small relief that my passenger didn't take the opportunity to act without my consent.  I was bewildered enough without any added complications, stunned, sore where the straps had pulled against my shoulders and gut.



``Kulshedra!'' Prefab shouted.  ``Lights on!''



``\emph{Auxilary offline.  Emergency lighting failed in six attempts carried out in two} seconds.''



``Uhhhh,'' he said, drawing out the sound, ``Damage report?''



``\emph{A.I. bank one offline.  Aux offline.  Propulsion offline.  Weapons offline.  Helm offline.}``



``Why are you speaking strangely?''  I called out.



``\emph{A.I. bank one offline.  Advanced linguistics, memory, geography-}``



``Enough,'' Prefab said, cutting it off.



I almost told him to let it continue, just so we had an \emph{idea}, but he was the boss.



``Protectorate, Wards, sound off!''  Prefab shouted.



``Arbiter.  Fine.''



``Vantage, mildly injured,'' Vantage said.  ``My hand.''



``Usher, bleeding from a bad scrape, but otherwise okay.''



``Weaver,'' I said, ``I'm fine.''



There was a pause.



``Leister?''  Prefab asked.



``Mostly okay,'' Leister said, but his voice sounded strained.  ``Took a hit to the gut.''



``Let's get ourselves sorted out,'' Prefab said.  ``If you can reach your phones, use them for light.  There's an exec on the second page, if you haven't mucked with them to add ten pages of games.''



``Don't--'' Leister said, still sounding odd, ``Don't diss the games, when you make us sit around waiting for stuff all the time.''



\emph{I didn't get a phone yet}, I thought.  \emph{But hey, I've got the damn butterflies.}



At my order, the butterflies that had been clustered on the outside of their cage took flight, spreading out over the ship's interior.



I spoke, ``Kulshedra.  Roof got crushed, lights with them, am I right?''



``\emph{Yes.}``



``No lights in floor?''



``\emph{Not at present.  Standard floor fixtures in Kulshedra model precursor were removed for containment box fixtures. Lights included}.''



``Any power to monitors?''



``\emph{Yes}.''



``Video footage of exterior, \emph{stat},'' Prefab ordered, cutting in.



Monitors flickered to life.  One in three showed only the ground beneath us, and another third were broken.



``Change the focus of any monitor displaying only asphalt,'' I said.



``\emph{A.I. bank one is offline.  Discrimination no longer possible.}``



``Monitors with video from any camera on the ship's upper half.''



``\emph{Restate, please,}'' the A.I. said.



``Nevermind,'' I said.  ``Um.  Nine working cameras, four on port side, five on starboard, am I right?''



``\emph{Yes.}``



I worked on unbelting myself, ensuring my legs were fixed in the bars beneath the bench, so I wouldn't fall.  ``Label monitors with numbers from one to nine.''



One by one, the monitors displayed numbers instead of the video feed.



``Weaver--'' Prefab said.  ``This isn't helpful.  We need information on our surroundings.''



``No immediate threats nearby, according to my swarm,'' I told him, checking with my bugs.  ``Ship, monitors one, three and seven weren't displaying a usable feed.  Restore a feed to each other monitor.''



The videos reappeared.



``Monitors two, six and eight are broken and are not displaying anything coherent.  Display white instead, maximum brightness, on those screens and any ones not displaying any video.''



Monitors lit up.  It wasn't much, but it was marginally better than what the Protectorate-issue phones were granting.



``How the hell do you know your way around this thing?''  Vantage asked.  I could see him below me, one hand outstretched, the other held behind his back.



``Defiant and Dragon have been ferrying me between the PRT and court, and between prison and these little field exercises, so I've gotten a sense of them,'' I said.  ``And I fought a bunch of others back in Brockton Bay.  You figure them out, kind of.''



``I saw that bit about Dragon's visit to Brockton Bay in the news,'' Vantage said.  ``Here, fall.''



I twisted myself around until I hung by my hands, then let myself drop from the bench.  Vantage caught me with the one hand.



The others were getting themselves sorted out.  A few minor injuries, but it wasn't as bad as it could be.



My head snapped around as our opponent landed just outside the ship.  She let go of her companions, setting them down on the ground beside her.



``\emph{Hellooooo},'' a girl's voice sounded over the system.  I had to turn around, checking all of the cameras, before I found the one where she was displayed, upside down.



``Ship, flip monitor, um, monitor four, one-eighty-degrees vertical,'' I said.



It flipped the right way around.  I could see a young girl on the opposite side.  She was flanked by two other small children, one a male with a widow's peak and a severe expression for his age, ten or so, the other a girl of about twelve, in overalls that ended at the knee, a star at the chest, and far too much makeup.



``Fuck me,'' Vantage muttered.  ``Bambina brought her team.''



``\emph{Come out and plaaaaay,}'' Bambina called out.  A second later, she leaped.  The small detonation that followed in her wake was quenched by the appearance of Rime's ice crystals.



``\emph{Sniper's active},'' Rime's voice came through the earbuds.  She was panting.  ``\emph{Deliberate, accurate shooter.  I've taken three bullets, ice armor took most of the force out of the shots.  Bambina is accompanied by Starlet and August Prince, um.  Shooter's shots ricochet.  Can't dodge.  There's wounded just outside craft.  Traffic caught underneath when you fell.}``



``Stop talking and get inside,'' Prefab said.



 ``\emph{Can't close the gap to the Kulshedra without getting shot again.  He's cutting me off}.''



``Use crystals to form a wall, get inside, damn it,'' Prefab said.



``\emph{Ricochets,}'' Rime stressed.  ``I- shit!''



I found her with my bugs, setting them on her costume.  ``She's okay, just fleeing from Bambina and Starlet.  The shooter doesn't seem to be targeting the kids.''



``My power makes her immune to Bambina,'' Usher said.



``Maybe to the explosions,'' I said, ``But the impact?  Or something else?''



He frowned.



``They're not on the same side,'' Arbiter said, ``The shooter and the child villains.''



``Good,'' Prefab said.  ``Let's-``



Bambina collided with the Kulshedra again.  It rocked, nearly tipping over onto one side.



``Kulshedra,'' Prefab said, ``Open ramp!''



The ramp opened, and I sent the butterflies out.  Nothing substantial, but it was \emph{something}.



Okay, not really.  But it was an opportunity to lay out some silk.  I emptied the reserves I had contained in my costume.



Prefab began working on a structure, forming it out of the same flashes of light and sparks of darkness he'd used before.  It took time to pull together, and the way it joined with the wall next to it, it didn't seem like he was designing it on the fly.



Similar to Labyrinth, but it was only natural that powers might run in parallel.



The shooter wasn't in my reach.  Bambina was horrifically mobile, bouncing off of walls and the street, creating explosions with most of the impacts.  Her teammates were along for the ride, apparently unscathed by her power.  Going on the offensive would be hard, even if I was using my full complement of bugs.



I was having a \emph{really} hard time justifying Glenn's rule on pretty bugs only.



Prefab's wall appeared around the craft.  ``Priority one is the wounded!''



We made our way out of the craft.  Odd as it was, I felt a mixture of relief and\ldots an emotion I couldn't place, at the realization that I didn't have to fight to convince my teammates that we had to help other people.



Three cars had been caught beneath the wings of Dragon's craft, another smashed by a chunk of ice.  The passengers of one car had fled, another two cars had people trapped inside, and the people in the fourth were unconscious.



I helped Arbiter with the unconscious ones.



``I alerted Dragon,'' Prefab said.  ``The Vegas teams know too.  This is a waiting game.  We help Rime, and we keep the prisoner contained.  If he gets loose, or if Bambina destroys the containment vessel, this gets a \emph{lot} more complicated.''



\emph{The prisoner}, I noted the word choice, \emph{not Pretender}.



``If I can get closer to the shooter, I can disable him,'' I said.



``Too dangerous.''



An explosion against the exterior of the wall Prefab had pulled together marked another attack from Bambina.



``I can \emph{do} dangerous.  Let me take the kid-gloves off, and-``



``\emph{No},'' Rime's voice came through my earbud.  ``\emph{No.  Stay.}``



I grit my teeth.  ``You're underestimating me.''



``\emph{We're well aware of what you're capable of.  }\emph{I'm doing you a favor},'' she said, and her voice was strained.  ``\emph{Stay, follow Prefab's orders.}``



I considered running, then stopped.  ``Okay.  I'm giving you some backup, Rime.  Best I can do.''



With that, I sent butterflies her way, clustering them into human-shaped groups.  When one group reached her, they surrounded her.  Decoys.



``Hard to see,'' she said.  I didn't even need the earbud to understand, with the butterflies near her.



I kept the bugs away from her face.  I wasn't sure that was ideal, but it was her call.



Arbiter and Prefab had enough medical training to check the civilians over before we moved them or moved them \emph{further}.  With my power, I tracked Bambina as she ricocheted through the area, causing innumerable explosions across the landscape.  Rime struggled to evade both Bambina and the detonation, while maintaining some degree of cover against the gunman.



``Last one,'' Prefab said.  ``Weaver, help.''



I helped him get the older woman to her feet, and keep her standing as we led her into the back of Dragon's ship.



I stopped abruptly, as Bambina's trajectory swiftly changed.



``Trouble!'' I called out.



Bambina landed atop the wall.  Her teammates landed beside her, each holding one hand.  They looked a little worse for wear.  Starlet was firing darts of light at Rime, the darts exploding mid-way through the air to block Rime's path when she tried to advance.  Between Starlet and the sniper, she wasn't able to advance.



 ``You were there for the Leviathan fight,'' I spoke to Bambina.



``Can't really bounce on water, it turns out,'' she said.  ``Wasn't worth the trouble.  Ducked out.''



Prefab let go of the older woman, leaving me with the burden as he faced Bambina square-on.  ``Lots of attention on Pretender all of a sudden.''



``Paying pretty well,'' Bambina said, ``And he promised a favor, too.  He set some rules, but considering how we're going above and beyond the call of duty, I'm hoping he'll bend them.  You know how fucking awesome it is to have a favor from a body snatcher?  He zaps himself into some hunky celeb that'd never touch me otherwise, then\ldots''



Bambina launched into a lewd explanation of what she'd have him do to her, and vice versa.  I averted my eyes and did my best to turn off my ears.  I'd started out spending months suppressing my powers to varying degrees, and I'd learned to ignore some sensations from my bugs.  I wasn't so lucky when it came to my hearing.



``\ldotswith my feet,'' Bambina finished.



Starlet, still firing on Rime, glanced over her shoulder to look at us, cackling at Bambina's audacity, while August Prince didn't seem to react.



I'd backed away, helping the older woman hobble forward on her bad ankle, and we were close enough to the ramp for her to make her own way up.  I stepped forward, my eyes still on Bambina.



``Worst thing ever,'' Vantage murmured from behind me.  ``Fighting kids?  You win, you get zero credit, no matter how good their powers are.  They're children, after all.  But if you \emph{lose}, well, they're \emph{kids}, your reputation is \emph{fucked}.''



``Focus,'' Prefab said.  ``We know who these three are.  We've got a Mover-shaker six, a blaster-shaker four, and a master-stranger three.''



``Hey, Weaver,'' Bambina called out.  ``You're that supervillain-turned hero, right?  Offed Alexandria?''



``Yeah,'' I said.



Odd, how I felt more at home in this situation than I had fifteen minutes ago.  Or even helping the civilians.  I'd \emph{liked} helping civilians, but this was where I felt most able to reach into myself and be strangely \emph{calm}.



``You fucked up my rankings for a straight \emph{week}, worst fucking time, too.  I'd planned an escapade, was supposed to rise to number \emph{thirty}, but your news took the front page instead, and I dropped to \emph{forty-five} instead.  I haven't been that low in a year!''



``Rankings?'' I asked.



``Rankings!  Don't you even pay attention?  It was \emph{embarrassing}.  My mom's still giving me a hard time over it, and it's like, that's less money from our sponsors.  So I'm going to make you deepthroat my fist, okay?  Break your arms and legs and make you suckle it.''



She stamped, and fire rippled around her.  Both August and Starlet flinched.



Worse, it destroyed the silk I'd been tying around her leg.



She leaped down, holding August Prince's hand, and Arbiter took action.  The heroine directed a sonic blast at Bambina with one hand, but Bambina kicked the wall, changing the direction she was moving.  Arbiter blocked her with a forcefield, then raised a hand to shoot again-



And stopped, standing still instead.  A look of consternation appeared across her forehead, above her mask.



Bambina ricocheted off of Dragon's craft, hitting it hard enough that it \emph{shifted}, then flew at Prefab.  One hit, and he was out of action.  The explosion hadn't even been that large.



Prefab, who had his cannon raised and hadn't even pulled the trigger once.



Bambina whipped around, rotating crazily before touching ground, her feet skidding on the ground.  She set the Prince down.  Starlet, up on the wall, laughed.



``Can't touch the Prince, can you?'' Bambina asked.  ``Go, August.''



The little boy advanced.  He held a scepter, different from Regent's.  More of a \emph{mace}.



Arbiter was backing up rapidly as he advanced, and I-



I thought briefly about what the heroes had said about Alexandria, about how she'd wanted them to act like the person they wanted to be.



I'd done that, in a way.  It reminded me of how I'd formed my identity as Skitter.  I'd acted fearsome, acted as if I \emph{expected }people to be afraid, expected them to listen, and they had.  Even Dragon had, at one point.



But maybe I didn't need to be feared here.  I could do something as \emph{Weaver}.  Confidence.  I didn't back down as the August Prince approached.  I sent butterflies his way.  No problem.



Tried to move them so he would be blinded\ldots and found they didn't listen.



Tried to bite and sting with the nastier insects I'd hidden inside the butterfly swarm, and again, no response.



He closed the distance to me, swinging at my knee with the mace.  I ducked back out of the way.



His fighting style was graceless, without any particular fluidity.  He held the mace with two hands and swung it, and then took seconds to recover.  An opening to strike, and my body refused to follow up on it.



That would be his power then.  Something in the same department as Imp's ability.



My bugs continued past him, and I sent them straight for Bambina.



She only laughed as the butterflies landed on her, stomped hard to kill most of them.  ``No way.  You offed Alexandria.  I'm not-  Ow!''



Bees, wasps and hornets stung simultaneously, targeting her eyes, mouth and earholes.



She stomped, and soared up to the top of the wall.  ``My face, fuck you!  This is going to swell!  This fucking\ldots''



I didn't hear the rest.  I was more focused on the little kid who was striving to cave in something vital.



The Prince swung at me, and I caught the mace.



It was a mistake.  He let go and tackled me, gripping my leg, hauling on it to put me off-balance.



I couldn't fight to pull him off, couldn't use my bugs.



This was annoying.



Then I saw Bambina point, saw Starlet stop taking potshots at Rime and turn my way, reaching.



If the Prince was the master-stranger hybrid, and Bambina the mover-shaker, then that left the \emph{blaster} power to Starlet.



``Arbiter!''



Arbiter threw a forcefield between us.  It didn't matter.  The dart of light she fired exploded against the forcefield, and the ensuing \emph{implosion} pulled me off the ground.  August Prince held on as I tumbled, then climbed up me before reaching around my throat.



I tucked my chin against my collarbone, preventing him from getting a decent hold, and he started clawing at me, struggling to get fingers, a hand, between my chin and my neck.



\emph{If this goes any further, Clockblocker's never going to let me live this down}.



The second thought was a little more grave.



\emph{If this little bastard kills me, the Undersiders will never forgive me}.



The others were helpless to assist me, due to the peculiarities of the Prince's power, but they could direct their focus to Bambina and Starlet.  Leister thrust out his trident, and it distorted, stretching the distance between himself and the two kid villains on the wall.  He struck Starlet in the face with the shaft of the trident.



Bambina kicked him, and he went flying to a point on the other side of the wall.  His spear distorted and brought him to the ground, but the kick- it hit too hard.  He didn't rise.



Seeing one of her Wards get taken out of action, Rime made a break for us, my decoys moving parallel to her.



The sniper fired, and she went down.  One guess, and it was accurate.



Tumbling through the air, she used her power in one singular burst, and was encased in a two-story high tower of ice.



Vantage leaped onto the top of the craft, then onto the top of the wall.  Starlet's blast nearly moved him.  Bambina leapt, bouncing off a nearby building, then flying towards Vantage.  He teleported out of her way, then threw a bola, catching her.  She fell from the wall, landing hard.



One down.  Two to go.



\emph{I'm better than this}.



The rules about interacting with the Prince were strictly defined.  I could hold him, but I couldn't hurt him.  Which category did silk fall under?  I had some on my person.  Twenty feet in all.  Twenty feet disappeared fast when it was wound around something.



I chose his neck.  Not hurting him, not directly.  His power allowed it.



One of Starlet's implosions sent Prince and I tumbling.  Too far from anything I could hold.  He found the opportunity to seize me by the neck.



``Someone!''  I said, ``Come closer!''



Usher approached, and Starlet blasted the ground behind him, pulling him off his feet.  He was mere handspans from where I needed him.



``Rime's out of commission!'' I said, my voice strangled as Prince did his best to choke me.  ``Your power isn't affecting her.  Give it to me!''



Usher focused his power on me.  I felt it ripple through me, felt \emph{something}, but it didn't break the spell.  I still couldn't turn the slightest amount of aggression towards the kid.



``No,'' I said.



Usher focused his power on Vantage instead, and Vantage flared with light.



Starlet's power hit him, and it didn't do a thing.  He punched her in the gut, then caught her as she went limp.



And Prince\ldots was harder to deal with.  Usher approached, and I tied thread around his leg.



I tried to tell Usher to \emph{run, }knowing what would happen with the thread around Prince's neck.  My voice wouldn't come out, and it wasn't due to the feeble but persistent attempt at strangulation.



So many heroes around me, and they couldn't touch this little bastard.



\emph{Move}, I thought.  \emph{Move, move, move}.



``Your power immunity isn't making me immune to the kid,'' Vantage said, helplessly.



\emph{Don't talk, move}.



In the midst of the Kulshedra, I could sense moving air currents.  A woman emerged from thin air, from a place cooler than the interior of the ship.  The civilians we'd rescued shrieked and backed away from her.  She didn't respond, barely reacted.  Someone with long, dark hair and a suit.  She fixed her cuffs, then moved with purpose.



But I found myself less fixated on her than on her surroundings.  Oddly enough, I could feel a different structure behind the woman, a hallway.



I tried to speak, but couldn't find the air.  Damn this little bastard.  Damn Usher for not \emph{doing} something.



``What a mess,'' Satyr called out.



Heads turned.



The Vegas Wards had arrived, perched on top of the nearest wall.  They didn't move to help, didn't leap to intervene.  Satyr glanced at Bambina, who was struggling to free herself from the bola.  There was something in his eyes.



Were they in on it?



``Help us!'' Vantage called out.  ``Rime's out, and we can't save Weaver!''



Satyr didn't speak.  He glanced at the ship.  He couldn't see from the angle he'd approached, but the woman inside had pulled the lever, and the door at the back was slowly closing.



I drew out words on the side.



Pretender in danger



The heroes turned, eyes going wide.  Satyr, Blowout and Leonid rushed forward, joined by Vantage.



Then Usher stepped forward to help, and the August Prince choked, giving me a little slack.  I sucked in a gasp for air.



Arbiter heard, whipping around, and threw a forcefield between us.  I pulled away.



She managed to sandwich the little bastard between her forcefield and the ground.  I rolled away, sitting up.



The ramp was nearly closed by the time they arrived.  Vantage slammed one hand against the door, but it was too heavily armored to give.



``Kul-,'' I gasped out.



The woman turned and walked up to the ruined nose of the craft, and began threading wires together.  She didn't even flinch as sparks flared between them.  She was measured, even patient, as she worked at fixing the panel.  When she was done, she tapped something out on the broken, unlit touch panel.



``Kulshedra, shut down,'' I managed.



``\emph{Restate request}.''



The pillar rose from the top of the box, freeing the upper part of the box's door.



``Kulshedra, contact Dragon,'' I tried.



``\emph{Dragon is currently unable to reply.}''



``Contact Chevalier.''



``\emph{Calling.}''



The woman tapped out another code, and the clamps on the bottom came open, freeing the bottom.



Yet another code typed out, and the system spoke, ``\emph{Type two safety override accepted.}''



The woman in the ship struck a single button.  The A.I. spoke, ``\emph{Call ended.}''



``Kulshedra, call Chevalier,'' I repeated.



Nothing.



The woman inside typed out a final code, and the door of the box opened, releasing Pretender.



And then she spoke, and I could hear through the bugs that surrounded her.  ``The Doctor will see you now.''



``Right-o,'' Pretender said.  ``Gotta be better than the Birdcage.''



They stepped through the gateway that led to the cool, air-conditioned hallway, and then they were gone, the butterflies in the hallway no longer in my reach.



I felt my blood pumping, roaring in my ears.  ``They got him.  They collected Pretender.''



``Who?''



``Her.  The shooter's partner.  Cauldron.''  I clenched my fist.  ``Rime's down.  We have to help her.''



``The shooter--'' Vantage started.



``He's gone,'' Arbiter said.  ``Not sensing a threat.  You guys go.  I'll look after Prefab and Leister, and make sure Weaver's okay.''



Usher nodded.



Satyrical gestured, and most of his team joined the L.A. team members.  I was left kneeling, still catching my breath.  Satyr and Nix hung back, arms folded, exchanging surreptitious glances.



Arbiter didn't look at them as she spoke, ``You hired them.  Bambina's crew.  You wanted to break him out.''



Satyr didn't respond.



``You were going to leave the Protectorate?  You had to have been.''



``Yeah.''  It was Nix who spoke, not Satyr.



``Just like that?''



Nix shook her head.  ``It's gone.  Doomed.  We lost Alexandria, we lost Legend and Eidolon.  The new team doesn't hit half as hard.  Look at Rime.  Taken out of action like that.  Protectorate's a shadow of what it was.''



``She was beaten by monsters the Protectorate refuses to even classify,'' I said.  I coughed a little.



``Alexandria would have managed.''



``Alexandria \emph{worked} for them,'' I said.



Nix shrugged.



Arbiter looked up at Satyr and Nix, ``If you leave, the Endbringers--''



Nix interrupted, ``We'll still fight Endbringers.  But the Protectorate was going to take Pretender from us because of how he got his powers.  It's ridiculous.''



``He was still going to be on the team,'' Arbiter said.  ``Just\ldots we can't let him be leader if he's beholden to a group like that.''



``It shouldn't matter.''



``Cauldron's \emph{evil},'' Arbiter said.  ``They experimented on people to get the powers Pretender has.''



``It doesn't matter,'' Satyr said.  His voice was rough.  ``Pretender's gone, and so are we.  We'll get our teammates and we'll go.''



He nudged Nix, and they turned to go.



One Protectorate team gone.



Arbiter dialed her phone, shifted restlessly.  ``Chevalier.  It's an emergency.''



There was a long pause.



``The Vegas team,'' she said, finally.  ``They've broken ranks.  There's more, but if we're going to arrest them, Dragon needs--''



A pause.



``No,'' she said.  ``They aren't.  No.  Yes.  Yes, sir.''



There was a defeated tone to her body language as she let her arm fall to one side, disconnecting the call.



Arbiter looked from her phone to Prefab.  ``Dragon collapsed just before this began.  She was meeting a Las Vegas Rogue.''



``Yeah,'' I said.  I thought of the woman who'd been so handy with the computer.  The censor, the bogeyman.  They'd taken out Rime, no doubt because she could have sealed the box behind a wall of ice.



Yet they hadn't taken out Prefab, who could have done much the same thing.



Every step of the way, every action perfect.



``The Vegas heroes?''  I asked.



``He said to let them go,'' she said, her voice small.  ``That we need them, even if they aren't Protectorate.  He'll send people to talk to them and arrange something later.''



I nodded, mixed emotions stewing in my midsection.  It was bad, it was \emph{disappointing}, to see a failure on this level, after I'd given so much up to help the Protectorate out.



``We lost on every count,'' I said.



``Rime's alive,'' Arbiter said, looking at her phone.



``Every \emph{other} count, then,'' I said.



``There'll be better days,'' she said.



\emph{Not like this}, I thought, and it wasn't a good thought.  As nice as the feeling of rescuing civilians had been, this was an ugly idea, a pit in the depths of my stomach.



The person I wanted to be, the person I \emph{was}, reconciling them wasn't so easy.  The hero on one side, Skitter on the other.



\emph{This has to change}.





