





``Mr. Chambers?  Weaver's here to see you.''



He called out from the opposite end of the room, ``Send her in!''



I ventured into his realm, staring around me as I entered the space that was apparently the hub of costume design and marketing for the PRT.



The wall to my left had a map of North America.  Cities had been identified, with clusters of portraits around each major city.  Protectorate members on top, Wards on the bottom.



To my right, there were glass cases showing off costume designs, old and new.  A woman was inside the case, dressing a dummy.



Further down, there was Glenn.



Power was a funny thing.  I'd seen it expressed in a number of ways, with parahumans, but the unpowered weren't quite so flexible.  There were people like Tagg, who relied on bluster and bullying, and people like Calle, with sheer confidence and a strict reliance on their own abilities in a particular field.  Piggot had been something else, someone who had known how to leverage people and situations, more like Calle than anyone, but with the added advantage that she'd had the authority to call in airstrikes and requisition Dragon's A.I. driven craft.  Like Tattletale had said, Piggot wasn't a genius, but she had her strengths.



I'd suspected that Glenn Chambers would be more like Calle, with a touch of Tagg's tendency to bulldoze through problems.  Seeing him operating in his home territory, I wasn't so sure that was the case.



Glenn Chambers wore plaid pants with red and green, and a pink dress shirt, His belt bore a buckle with the PRT logo on it.  His hair had changed too, parted neatly into what I assumed was `geek chic', and the glasses had changed as well, with thick, round frames.  An ID card hung around his neck.  He didn't fit any of those particular archetypes.



I looked at him and the person who came to mind was \emph{Skidmark}.  Brockton Bay's onetime loser villain, meth-head and drug dealer, later the head of the depraved, anarchist Merchants.  It was hard to pinpoint why, at first.  They were nothing alike, on an aesthetic level.  Their demeanor, their status in society, their appearance or goals, there were no similarities.



People milled around him.  Twenty-something men and women, who carried coffees and portfolios, cloth and paperwork.  Fat as he was, Glenn moved swiftly.  He sipped a coffee, handed it back to the assistant who'd delivered it, and sent her off with a command or clarification.  Men and women with portfolios were told to set up at his desk while he examined action figures in the light of the window.  His pudgy hands, almost childlike, took hold of an action figure by the arm.  He shook it violently, his cluster of minions backing away at the sudden flailing of his arm and the plastic figure.  The arm snapped off, and the toy went sailing through the air.  Someone scooped it up and brought it back to the group.



``Go, and hurry,'' Glenn said.  ``Tell them to fix it and cast another prototype before the run starts.  These are \emph{toys}, they'll be in the hands of children and collectors both.  The people who are buying these are \emph{fans}.  What's it going to say if their most \emph{immediate} association with Esoteric is the broken toy sitting on a shelf?  It's going to convey that he's \emph{flimsy}.''



The action figure people fled, and Glenn approached his desk, where the portfolios had been set out.  I approached, a touch lost in the midst of all of this, and nearly stumbled as another group entered the room, vacating to fill the void left by the group that was exiting.



``Weaver, come.  Look and tell me what you think.''



I approached the desk, and the group parted to give me space.  It was hard to put my finger on \emph{why}, but I couldn't help but feel like they were doing it at Glenn's bequest and not mine.



The massive portfolio folders were open, showing poster images of various Protectorate members.  The leaders of the new teams.  The images were stylized, with splashes in pale watercolor in the background, an almost sketchier appearance to the heroes.  But the masks, necks and shoulders, the emblems and their characteristic tools were all done in hyper-realistic detail.  Chevalier, Rime and Exalt, with backgrounds in gray, blue and yellow, respectively.  There looked to be more behind them.



``They're good,'' I said.



``They're crap,'' Glenn countered.  One finger tapped on a blossoming of yellow and red watercolors at the tip of Chevalier's Cannonblade.  ``The last thing we want to convey are that things are a \emph{mess}, and that's exactly what the blobs in the background will do.''



``\emph{I'd} buy one,'' I said.  ``If I wasn't already a cape, anyways.  Things \emph{are} a mess.  I don't see how you'd convince a non-cape me otherwise.''



Glenn sighed.  ``We're treading into philosophical and hypothetical territories there.  It's a no-go.''



He turned to one of the artists,  ``Something cleaner, tighter.  And don't use a side-profile of Rime.  If she doesn't want the post-effects, she'll have to accept that her waist isn't quite poster material.''



The poster people disappeared, fleeing Glenn's presence.



I stepped into the gap, ``I wanted to talk to you-''



``One minute,'' Glenn dismissed me.  He turned to the group that had just arrived, ``The interview?''



``It's good,'' a young man said, handing over a print-out.  ``Chevalier is personable, but different from the old leaders.  Fits the `New Protectorate' atmosphere you described.''



``Of course it does,'' Glenn said.  He skimmed the paper, turning pages.  ``I based it all around him.  Good call on the interview's quality.  Quite good.''



\emph{Skidmark, } I thought again.  Skidmark, who had built up a kind of momentum around himself, like-minded people falling into his orbit.  Despite being utterly repulsive and foul-mouthed, Skidmark had \emph{charisma}.  People followed him.  Glenn wasn't \emph{repulsive}, but he grated.



Maybe that was part of their charisma.  Maybe the natural, casual narcissism, as much as it didn't jibe with Skidmark's meth-mouth or Glenn's obesity, conveyed that they were the center of the universe.  \emph{Everyone} wouldn't necessarily be swept up in their delusion, but the fact that they drew in weak-willed sheep lent them a measure of clout that forced people to acknowledge them.  For Skidmark, it had been depraved homeless, addicts and thugs.  For Glenn, it was a cadre of college students hoping for a career in marketing, advertising or public relations within the PRT.



Or maybe I wasn't thinking too generously about Glenn Chambers, given how pissed I was.  Maybe he wasn't \emph{that} bad.



``Well?'' he asked me, as if I was making \emph{him} wait.



I resisted the urge to react, forced myself to stay calm.



If he was really like Skidmark, in how he surrounded himself with loyal and terrified sheep and minions, there were two ways to mount an attack.  I could take the fight straight to him, like Faultline had with Skidmark, or I could strip him of his flock.



``I'd like to speak to you in private.''



``Impossible, I'm afraid.  I'm busy enough I shouldn't even be taking the time to talk with you,'' he said.  He offered me a smile, ``But you're my most interesting project.''



``It's a matter of courtesy,'' I said.  He wanted to play this on a political level?  ``\emph{Please}.''



\emph{Put him on the spot.  Force him to play along or look bad}.



Glenn only smiled.  ``Isn't it just as discourteous to interrupt me in the middle of my work, when I'm already doing you a favor by meeting you?''



Fine.  He wanted to play it that way?



``Last night, Pretender got broken out of Dragon's craft, our team crushed, and Rime shot.  I almost died.''



``I heard,'' he said.  He looked at the woman who was just arriving with his new coffee, ``Kayleigh, can you go talk to Mr. Payet?  He was supposed to call me in ten minutes and it's been fifteen.''



``Yes sir,'' she said, running off.



\emph{He either doesn't care or he's deflecting}.



``Your insane restrictions on powers were a big part of that, Mr. Chambers.  The bad guys won, and it's partially your fault.''



The heads that turned my way, silent and staring, only confirmed my suspicions.  The crowd of twenty-something assistants and designers around him were a defense system.  Not a \emph{power}, but power in general.



``My fault? I wasn't even there.''



``I asked to speak to you because I wanted you to know about the damage that's being done.''



``Ah, this is about the butterflies.''



``It's about a lot more than butterflies.  It's the whole mindset.  The attitude of the heroes.  I'd talk to Chevalier, but he's too busy.  I'd talk to Rime, but she's recovering from being shot three times.  You're the only other person I've met so far who really seems to be in a position to know what I'm talking about.  Besides, as far as I can figure, image and PR seem to be at the heart of the problem.''



``A complicated issue, something you could study for six years in college,'' he said.  ``But you've figured it out after two brawls?  The rumors of your intelligence must be true after all.''



``I wouldn't make light of it.  Pretender got captured.  Either he's in enemy hands, and there's a body snatcher out there, or he's dead.  Because of a fight we could have won.'' I said.



``You're sure?''



``There're no certainties, but come on.  There's got to be a point where the kiddie gloves come off and we actually put up a fight.  I saw the Wards struggling in Brockton Bay, as they faced pressure from outside forces, \emph{me included}, and serious threats.  They got whittled down because, as powerful as they are, they didn't get the chance to put up a fight.  Now the rest of us are starting to face the same pressures, and the PRT isn't learning from past mistakes.''



``I'm trying to understand what you're wanting to argue.  Are you saying our Wards, children with powers, should take your cue?  Fight more viciously?  Intimidate?  Be merciless?''



``\emph{All} your capes could stand to stop holding back.  Wards and Protectorate both.  At least in situations like this.  We lost Pretender, and we didn't exactly inspire confidence in the Vegas teams.  That played a part in losing \emph{them}.''



Glenn frowned, glancing at his collection of underlings.  ``Everyone but Weaver, out.  I hope each of you can find \emph{something} to do.''



The flock scattered.



``You already know what happens if you speak on the subject,'' Glenn called out to them, raising his voice as they got further away.  ``I personally know \emph{everyone }you might try to leak details to.  It's not worth the risk!  Discretion!''



A moment later, they were gone.  His office seemed so empty without the young professionals running around.



``We \emph{must} have a talk about which things can be said when\emph{,'' }Glenn said.  He took a second to tidy up stray pictures on his desk.



``I did ask if we could speak alone,'' I told him.



``And I said no.  I'm much too busy, and as much as I relish our future discussions, hearing how you did what you did in Brockton Bay, the Vegas Wards are a large part of why I'm racing to provide the public with our new, \emph{upgraded} Protectorate.''



``Misdirection and deception,'' I said.  ``You know, I \emph{do} know about subtlety.  I kind of ran a group that ruled a city.''



``And I'm sure you did an excellent job,'' Glenn said.  ``But you're a dog in a duck pond here.  You're out of place, you don't know the usual precautions, the customs and conventions.  You gave evidence to that when you talked about the Vegas wards, something that should be kept more discreet.''



That would be his mode of attack then.  I was the ignorant child, who didn't quite know how the Protectorate worked.



``I'm not sure what you want, Glenn.  You guys \emph{know }I can hold my own, but you ignore the fact that I took down Alexandria, that I've fought against \emph{three} class-S threats.''



Glenn sighed.  He walked around his desk and plunked down in his chair.  ``You're going to be one of the challenging ones, aren't you?''



``I only want to help people.  The PRT and the hero teams are falling apart, but you're more focused on testing me than letting me \emph{do} something.''



``Chevalier would be a better person to talk to about this,'' Glenn said.



``You want me to fight with nerf weapons?  I can.  Put me up against just about any Ward, I could probably give them a pretty hard time, whether I'm using regular bugs or just butterflies.  I could win against most.''



``Your strength isn't in question.  We're not sure you're dependable.''



``I can show you that I can make the butterflies work.  I just want the a-ok to use my \emph{full} assortment of powers against the real threats.  Like the sniper and whoever that woman in the suit was, last night.  If I'd had a \emph{rea}\emph{l }arsenal in reserve, I could have attacked either of them before they really get underway.  Give me the ability to match the strength of the tools I'm using to the strength of my enemies.''



``Beginning an endless loop of serial escalations,'' Glenn said.  ``No, Weaver, that's not what I mean when I say `dependable'.  Wrong word.  We have footage of you \emph{snapping}, shifting from calm to homicidal in an instant.  Was there motivation?  Yes.  But it doesn't inspire confidence in your allies.  We wanted to see how you functioned in high pressure situations, your willingness to follow our restrictions, as unfair as they might seem.''



``Always testing me,'' I said.  ``Okay.  I listened, I followed your orders, and the test doesn't serve a purpose as long as I know about it.  Can we call it quits, at least with the butterflies?''



``You didn't follow the orders,'' Glenn said.  When I glanced at him, he locked his eyes onto mine.  ``You stung Bambina.''



``To \emph{save} people.  She was going to pick us off.  Would you blame me if I picked up a dropped gun and shot someone who was aiming a surface-to-air missile launcher at me?''



``It's a little different.''



``It's an almost exact parallel to what I was doing!  She's a living surface to air missile, only she ricochets all over the place, and she keeps going.  I didn't even use a gun.  I debilitated her, maybe enough that Vantage could hit her with his bolas.  Nonlethal weapons, exactly like what the Wards are supposed to use.''



``The focus isn't on lethal or nonlethal,'' Glenn said.  ``It's on whether we can trust you to keep on the path you're walking.  If you start taking shortcuts now, what happens a year down the line?  If we decide you can go all-out in one specific situation, does that open the door for another?''



``Maybe, instead of setting rules and restrictions in place, you could \emph{ask}.  Talk to me like a human being, negotiate certain rules.''



``Rules you then break or circumvent.  You take rather naturally to it, and \emph{no}, that isn't a jab at your \emph{iniquitous} background\emph{.  }It's a statement about your particular abilities.''



I grit my teeth.  ``I'm \emph{good}.  I have more experience than some of your Wards who've been on their teams for two years.  I'm versatile.  If you need someone in Vegas to deal with thinkers and strangers, I can hold my own, the embarrassment with August Prince aside.  If you need someone to track down groups like the Nine, I can do that.  Recon, assassination, communication\ldots''



``The public's watching this too closely for us to let you off your leash so soon after Alexandria's death.  When things quiet down, it might be a possibility.  Our heroes in Vegas tend to be a little grayer than white, and an ex-villain would fit.  But not now.''



I exhaled slowly.  ``You guys wanted a newer, shinier protectorate.  You guys need wins.  Give me the chance, I'll give them to you.  But this isn't \emph{me}.  I'm not about butterflies.''



``We know what you're about,'' Glenn said.  He touched his keyboard, then typed out what I presumed was a password.  A second passed, ``Look.''



He spun his monitor around.



It was me, entering the PRT office in Brockton Bay.  A video feed from a surveillance camera.



It was me, crawling through a window.  That would be from the night I retaliated against Tagg.  Odd, seeing how the bugs moved in coordination with me.  When I turned my head in the video, the orientation of every bug in the swarm changed in the same moment.



All around me, PRT employees were howling in pain, their cries silenced by the lack of an audio feed.  Either the camera hadn't picked it up, or Glenn had muted it.  They thrashed.  One reached for me, for the \emph{me} on the screen, and I could see how I moved out of the way without even glancing at him.  The swarm concealed me at the same time, briefly obscuring the Skitter in the video from both the man on the ground and the security camera.  When it parted, she had shifted two or three feet to the left.  A simple step to one side in the half-second she couldn't be seen, but it misled the eyes.



And I couldn't remember doing it.  I'd never consciously added the trick to my repertoire.



``If you told me that girl was a member of the Slaughterhouse Nine,'' Glenn said, ``I wouldn't have batted an eyelash.''



It was like hearing my voice played back to me, but it was compounded over several levels.  The movements, the movements of the swarm, it wasn't familiar to me.



The head turned towards the security camera for a moment, and I could see the yellow eyes of my lenses in the midst of the thick black swarm.



``That isn't marketable,'' Glenn said, oblivious to just what I found so bothersome.



``There's a middle ground,'' I said.



``When I asked you to use butterflies, it was to break a habit, see if it changed how you functioned in the midst of a fight, just like I might ask someone to try on a particular outfit and see how it fits them.  I didn't think it would throw you off kilter as much as it has.  But that isn't a bad thing.''



``It is if it means Rime nearly dies and Pretender gets taken.''



``We collected the three members of Bambina's group.  Not a complete loss.''



``They'll get free and continue their rampage,'' I said.



``Most likely.  We'll strive to hold on to Bambina at the very least.  With luck we'll be able to recruit the little prince, maybe Starlet as well.''



I looked at the video.  Glenn had paused it.  The momentary turn of the head, the yellow lenses\ldots



``I can work on being a little less nightmarish,'' I said.  ``But there's got to be a way for me to be more effective.  How long are these restrictions in effect?''



``Until you come of age and join the Protectorate,'' a voice spoke from behind me.



It was Chevalier, accompanied by Defiant, my ride.  Chevalier wore his gold and silver armor, heavily decorated and etched until every square inch looked like a miniature work of art.  It didn't strike me as something that would hold up to any abuse, but I'd heard how tough it really was.



``Until I turn eighteen,'' I said, feeling a little hollow.



Chevalier approached.  ``You murdered two people.  Three, going by your admission while in custody.  Two PRT directors, one major hero.  When Dragon and Defiant suggested we bring you on board, we were divided.  It was \emph{Glenn} who offered the compromise that we ultimately agreed to.  \emph{This} compromise.''



I glanced at Glenn, who shrugged.



\emph{Glenn}?



``You have blood on your hands.  We need to know that you can hold back, that you won't simply \emph{snap} as you did when you were in custody in Brockton Bay.  We're still wanting to ensure that this isn't a long-term scheme on the Undersider's part, as unlikely as it might be.''



``\emph{That's} why you're waiting two years?  You think that it'll take that long to vet me, before you can give me actual responsibility?''



``It's one consideration of many.''



``It's ridiculous.  The world is going to \emph{end} before I have my eighteenth birthday.  I'm giving you full permission to \emph{use} me.  Send me to round up tinkers who could find the Nine's pocket dimension\emph{. } I've been a villian.  I've got some reputation I can fall back on.  I can talk to people you guys can't.''



``I won't say this is set in stone,'' Chevalier said.  ``Maybe in a few weeks or a few months, we can discuss options.  For now, we'll find you a team, get you settled.  Once we know where we're situating you, we'll find a different institution to keep you in.  Possibly low security, or in the Wards headquarters, depending.  The rest\ldots there's time to figure that out.''



I sighed, closing my eyes.



``I'm sorry,'' Chevalier said.  ``Really.  I was there for the fight against Echidna.  I saw the Undersiders in action.  I saw \emph{you} in action, and I'm willing to credit you with the maneuver that turned the situation around in the final stages.  As long as your rap sheet may be, I've heard of the good you did.  It strikes me that you've likely saved one person from death and injury for each person you've assaulted, if I were to count what you did before Shatterbird hit your city.''



``But that doesn't matter in the end.''



``It does.  More than you suspect, but you have to be \emph{patient}.''



``You've faced a great deal in the span of half a year,'' Defiant said.  ``Take this for the reprieve it is.''



I grit my teeth.  No use.  The legitimate avenues were failing me.



I couldn't put up with this.



``Then there's one last thing,'' I said.  ``If I can't help directly, let me help indirectly.  I can outfit your heroes.  Most of them.''



Glenn and Chevalier exchanged glances.



``We were going to raise the idea somewhere down the road,'' Chevalier said.  ``We can work out a deal, like we have with our tinkers.  An allowance, with payment for each costume produced.''



``I don't want money,'' I said.  ``But so long as you're offering, maybe we could talk about a workshop?''



I glanced at Defiant, ``And equipment?''



\sectionbreak



Spiders moved through the back corridors of the prison.  It was a space where the plumbing and heating for the two interconnected prisons ran through pipes, and where the flooring was little more than metal grates, easily removed and replaced in a pinch.  Almost lightless, but that didn't bother me.  My spiders could manage, and it only meant I had some time to hide them if someone entered and hit a switch to turn the lights on.



I'd thought of `Weaver' as a hero on the straight and narrow.  That was out.



Being a villain with good PR just wouldn't work either.



No.  A middle ground, then.



The spiders found a rat.  It backed away from the mass, hissed.



A spider dropped on it from above and delivered the first of what soon became a series of bites.  Fatal.



Working together, the spiders set to devouring it.  They weren't natural scavengers, but meat was meat.  Meat meant the spiders could get the sustenance they needed for breeding.  Breeding, in turn, meant I could start mass-producing silk.



It was calming, a relief to do something concrete after an afternoon in Glenn Chamber's company.  When the time came, I could carry any materials and the spiders onto the bottom of the Pendragon, moving them to my workshop.



``Hebert,'' the guard said.



I raised my head.



``Mail day.  You're a popular one.''



It was a \emph{bundle} of mail, bound together with tape marked `USPS'.



``They're already open?''



``Rules.  We don't read it, or we're not supposed to.  But they check there's nothing illegal inside, and the dogs give it a sniff.''



I nodded.  She studied me for a second, then moved on to the next cell.



Mail from all around the United states.  From strangers, from \emph{fans}.



Words of support.  Criticism.  Death threats.



I opened the ones from Brockton Bay last.



Taylor.  Weaver.  Skitter.  Is it bad that you'll always be Skitter to me?



I could hit you, hug you, yell at you and hold onto you for hours all at the same time.  It's fitting that I want to kiss you and throttle you at the same time because that's what you were to me for a long time.  You drive me crazy and I can never understand what's going through your head.



This isn't easy.  I'm not good at this.  Not with where we left off.  It felt like an incomplete break, but I don't think it would be much better if we were still together or if we'd broken it off completely.  I'm not the type to write heartfelt letters.



I hope they don't read your mail and give you a hard time because of this.  I'd erase that part but I've already started over three times.



What ever am I even supposed to write?  That I want to yell at you because I told you I couldn't be leader and you left anyways?  That you shouldn't worry and Tattletale and I have it covered?



You're an idiot.  I want you to know that.  You're an idiot, Skitter.  You're brilliant and reckless and I'm betting it makes sense to you to do this but you're an idiot.



I'll write again, when I can figure out what to write.



Grue.



I read it three times.  I could almost hear his voice.



I opened the next one.



HAHAHAHAHAHAHAHAHAHAHA!!!! what the fuck???



There was only a little circle with devil horns at the bottom, in place of a signature.  I rolled my eyes and moved on.



Tt here.



You probably want to know the situation.  We're all alive, Accord hasn't turned on us yet, things are getting more exciting but we'll manage.  Heroes are leaving us alone, like you arranged.  Trick will be to get Regent and Imp to stop prodding them for reactions when they cross ways.



Heartbreaker making initial forays, decided to pay a visit.  Can't tell if he's invading or after Regent.  Red Hands are a little more aggressive but not too bad.  Meeting for negotiations tonight.  Lost Garden approacheth, sending members after us and trying to clear way for Barrow to advance.  Annoying but no problem until they enter city limits.



Grue wasn't okay at first.  Worst days since right after Bsaw.  He won't say in his letter but you would want to know.  Got better when Red Hand and Heartbreaker came.  Busier, something to do other than wallow.



Regent&Imp constantly together.  Mucho annoying since you gone.  They're testing the waters, seeing what they can get away with.  Will see how it turns out.



We got Flechette.  She a pair with Parian.  Lovey-dovey.  Best case scenario, really.  Not sure if you arranged that, good call if you did.  Flechette's going by Foil now.  Likes those F names.



My head's better as of yesterday.  Tryng to take it easier.



Managed to get hold of Rachel.  She said she'd send letter.  She can't read/write but she insisted she would anyways.  Interesting to see how that turns out.



Everyone on edge of their seat waiting for Endbringer to hit.  Won't be Bbay but we participating.



See you there, hun?



P.S.  To the asshats reading Taylor's mail, there's no codes in this message.  Promise.  Don't bother.  You want to know what we're up to, call me.  I'll fucking tell you.



P.S.S.  Gathering all letters together, 12 hours ltr.  None from Reg, he said to say hi.  Meeting with Red Hands went ok.  No alliance but nonaggression pact mebbe



I took it in and sighed.  There were no less than three villainous groups converging on the Undersiders, and Grue had been in bad shape.



And yet it was still reassuring.  Things were, for better or worse, normal.  Much as I'd expected.



Atlas died.  I wanted to let you know.  Tattletale had him, but he wouldn't eat or move.  We asked for him, and we found a place for him.  The guys say they think they know a good way to make a mold.  They're covering him in brass.



A way of saying you're still with us.  Take care of yourself.



-Char



It affected me more than I would have thought.  Not him dying – he'd never been more than an automaton, a freak of nature made to do little more than obey my commands.



But it was one more tie to the Undersiders that had broken.



The last letter was handwritten in a spidery script.



(She said to write what she said.  All of it.)



(She hasn't said anything for a long while.  She growled at me when I started to walk away tho.  Oh here.)



I did what you said.  Is quiet.  Have tents and dogs and am hunting with dogs.  Hunting fucked up bull things.



(Bison)



Very quiet with no people.  Learning to cut them up.  (The bison not people).



People are cutting down trees to clear space around portal, but easy to stay away from them.  Simple way to live.  Nice but miss toilets.



(We all miss toilets)



Tattletale visits, brings dog food and tools, tents.



Is what I wanted for long time.  Except others, my people, but they are okay and I can take a break and ride for while if they get on my case.



Being around you wasn't simple or quiet but things made more sense.  Your minion with dark hair said we need to be around people but I'm around people and still feel somethings missing.



Fucked up.  Makes me angry.  Tattletale tried explaining but whatever.



Going to take puppies to your place again soon.  Show the kids to them.  Might help.



You have plan, okay.  But if your plan means you're thinking about fighting us you should know I am getting very good at hunting and skinning things.



Sucks somehow but can't really understand why.  Maybe see you at next Endbringer fight.  We both stay alive.  Try hard.



That's all.



(Signing off – Rachel and Rachel's excellent minion/henchperson/letter writer)



\emph{Stay alive until we can see each other again?}



Doable.



`Try hard'?



Maybe that was the push I needed, such as it was.



I collected the mail, wedging it into a space between two of the library books on the little table in my cell.



Withdrawing a notepad, I started sketching out the designs I was thinking of.  Alterations to the costume, weapon ideas, tools and concepts.



\emph{Payloads for bugs?  Something I can drop?  Caltrops?  Something toxic?}



Back to my roots, to where I'd been after my powers had manifested.  Only then, I'd been writing in a black speckled notebook.



\emph{Darker fabric?  Must talk to Glenn about costume style.  Butterflies are in, but can I complement them?  Need official word}.



It was moronic to have a white costume.  Equally moronic to have butterflies.



What about containment foam?  If Dovetail can use it what does it take for me to get permission?



I'd pay homage to Atlas and push Defiant and Dragon to create something that would let me fly.  Pay homage to \emph{Skitter }and settle on a middle ground in costume design, in combat effectiveness, weapons and utility.



I thought of Atlas, and added a note – \emph{jetpack?  With beetle wings?  Flight system?}



I was nearly through the pad, and it was pushing four in the morning by the time I had the sketches and outlines at an acceptable point.



The costume Defiant and Dragon had given me was theirs, not mine.  The fighting style that had been dictated was Glenn's and Chevalier's.



\emph{This}, this would be me.





