





``I'm so sorry I'm late.  I never do this,'' Mrs. Yamada said.  She entered the office, a raincoat, boots and a messenger bag in her arms, her hair a touch damp, clearly flustered.  ``What a way to start us off.  I'm so embarrassed.''



``It's okay,'' I said.  ``It's not like I'm going anywhere.''



I knew right away that it wasn't her office.  It just didn't fit her, in any sense.  She was average in height for a woman, which put her a little taller than most Japanese women, her hair cut short in what I took to be a utilitarian choice, but was styled enough to show a degree of effort.  Her clothes and shoes were much the same.



The room, by contrast, clashed with her demeanor.  There was a level of \emph{care }that went into it.  Like, I couldn't help but feel that the desk in the corner and the chairs were antiques, or at least very expensive.  There were model airplanes on the shelves and pictures of airplanes on the walls, and Mrs. Yamada didn't give me the impression of an airplane afficionado.  The sheer \emph{heft} of the chair and desk seemed out of proportion with Mrs. Yamada as a person.



Was she borrowing a colleague's office?  For the last while, I'd been ferried here and there.  Dragon and Defiant were my custodians, and between them, they were traveling all over America, making it relatively easy to schedule a pick-up and drop-off.  It was almost easier for me to go to Yamada's office than for her to come to me, but we'd come here instead.



``It's a matter of professional courtesy,'' she said, more like she was talking to herself than to me.  She was still getting herself sorted out, her raincoat hung up, rain boots replaced with slippers she'd been holding beneath the coat.  ``Being prompt, it indicates that I respect and value your time.  You can't confide in me if I don't respect you.''



\emph{Respect me?}



I looked down at the floor for a moment.  She was looking at me when I raised my eyes to her.  ``With all sincerity, it was due to forces entirely out of my control, with complications at every turn.''



``Bureaucracy,'' I said.



``You're not wrong,'' she said, ``But it was something else.  A patient of mine, institutionalized, she's reacted badly to certain events in the last month.  Someone she idolized left the Wards, and-''



I could see her stop, composing herself, the stress and preoccupied attitude melting away.



``-And this isn't about that.  This session is about you.''



``About me.  This could be a long session,'' I said.



``My instinct,'' Mrs. Yamada said, as she settled uncomfortably into the large, somewhat ostentatious chair, ``Would be to ask about the little details you've seeded into the conversation already.''



``Details?''



``How you seized the idea that it's \emph{bureaucracy} that would be holding me back,'' she said.  ``Or your facial expression when I said I want to approach this meeting with \emph{respect}.  But there's other points I think we should cover first.  We'll get back to that, if you're interested.''



I shrugged.



``FIrst off, let's start off with the basics.  How are you?''



\emph{Pretty basic}.  ``Fine.''



``You're in prison, and will be for at least two years, maybe longer.  By all reports, you're chafing under the new restrictions you face as a member of the Wards.  That's without touching on the fact that, two weeks ago, you murdered Alexandria and Director James Tagg out of fear for your safety and the safety of your friends and teammates.  In this room, or wherever we go to talk, it's okay to answer `how are you' with an admission that you're \emph{not} okay.''



``I'm- I feel better, after talking to Glenn and Chevalier.''



``How did you feel before?''



``Restless.  I still am, really.  Very restless.  If one feeling is taking hold of me, it's that.''



``How so?''



``Before I was in jail, I ran every other morning.  I can't run now, but my body still wants me to, at the usual time and the usual pace.''



She nodded, making a note.  ``When did you start?''



``About a month after I got my powers.  February.''



She nodded.



I went on, ``And there's the other stuff.  You might not believe me, but I was \emph{helping} people.  Hurting people from time to time, but mostly helping.  I was getting food out to people who were hungry, checking everyone had what they needed, laying long-term plans for the future, so that people who've never had a chance in their lives would finally get one.  I'm helping people \emph{less} now that I'm going out with the Wards.''



``Do you think that maybe you're hurting people less?''



``But the sum total is \emph{worse}.  It's like, if you go back to the very fundamentals of right and wrong, you have to ask, `if most people acted the same way I'm acting right now, would society be better off?'''



``Okay,'' she said.  ``And you think society would be better off if everyone acted like you?''



``Sort of,'' I said.  ``Yes, I hurt people, but I hurt people who deserved it.  When I had the resources to do it, I helped a lot of people.''



``In this hypothetical reality where most people think like you, correct me if I'm wrong, transgressions would be punished?''



``Yeah,'' I said.  ``Guess so.''



``Would it be fair to say they're punished harshly?''



She was thinking of Alexandria and Tagg, no doubt.  Maybe Valefor.  ``Yeah.''



``Kind of medieval, isn't it?''



It reminded me of my dad, that idea.  ``Guess it is.  But capes are naturally violent.''



``And what about the Wards?  I wasn't there at the time, but one of my colleagues started seeing the Brockton Bay Wards a short time after Leviathan attacked the city.  Did they commit a transgression that warranted the pain they suffered at your hands?  The ones that aren't Shadow Stalker?''



I didn't have a ready answer to that.  She waited in silence for long seconds before I shrugged.  ``There was stuff, the fact that they tolerated people like Shadow Stalker, but I'm not sure I could explain it now.  Feels like a long time ago.''



``A lot's happened all at once.  It might contribute to the restlessness you feel now that things are quieter.  You said you felt better after you talked to Glenn and Chevalier.  Why?''



``I got a chance to talk stuff through.  More of a sense of \emph{why} they were putting obstacles in my way.  And on my way over here, I gave Dragon some notes on an updated costume and gear.  She'll probably email it out, they'll discuss the options and tear the proposal to shreds.  If they accept \emph{any} of it, though, I'll bring me a step closer to being \emph{me}, to being more comfortable with what I'm doing.''



``That's a good lead-in to the next big question I had in mind.  Who are `you'?  I make a point of asking all of my clients this, but what should I call you?  Weaver?  Taylor?  Skitter?''



``All of the above?  Maybe call me Weaver.  I'm still trying to get used to the name.''



``Okay, Weaver, and my next easy question is whether I can get you anything?  Water?  I remember you had a coffee cup in front of you in the interrogation room in Brockton Bay.''



``It was tea,'' I said, ``And not right now, thanks.''



``Okay,'' she said, making another note.



``Writing down some profound insights?'' I asked, gesturing towards the pad of paper she had in her lap.



``Details about you, your tastes and priorities.  Maybe I'll have tea ready the next time we meet.  Black, green, herbal?''



``Black.''



``Okay,'' she said.  Another brief note.  ``This is the first date, Weaver, if you'll excuse the metaphor.  This is when I get a sense of who you are as a person, the fundamentals of who you are.  I then use that to help you and inform you.  You aren't obligated to take my feedback without question, or to take my advice as orders, but if we wind up being a good team, then hopefully you'll \emph{ want} to, because you find it genuinely helpful.''



I nodded.



``I know only a little about you from context, but I don't want to be one of the people who jumps to conclusions about you, so I'm second guessing every detail that you don't personally share with me.  I drew up a timeline, which was why I asked when you started running, trying to get a sense of what was happening for you and when.''



``Any insights?''



``Some, but we can talk about that another time.  Later today, maybe.  My point is, I'm trying to figure you out.  So please forgive me if any of my questions seem too simple, or if I'm asking about things I should already know.  The next set of questions are a little more serious.  Do you \emph{want }therapy?\emph{``}



``It's kind of obligatory,'' I said.



``I'd change my approach depending on whether you hated this but were playing along, if you really \emph{did} want help figuring things out, or if you wanted therapy but didn't want it with \emph{me.}''



She let that last bit hang in the air.



When I didn't respond, Mrs. Yamada said, ``I would understand if you felt like you had to be on guard against me.  When you were dealing with the Protectorate and PRT in Brockton Bay, it might have looked like I was one of the enemies.''



``You were pretty decent to me, all things considered.''



``Good,'' she said.  She smiled a little.  ``Thank you.  Let me pose the question another way.  You've said you're able to tolerate my presence?''



I nodded.



``Okay.  Given that you've accepted me, I'm wondering what you think my goal is.''



``You're going to report back to the guys in charge of the PRT and the Protectorate and tell them whether or not I'm of sound mind, whether I can join the Wards team without snapping and murdering someone.''



``That's not it,'' she said.  ``In fact, I may well do the opposite, depending on how this meeting goes, and avoid commenting altogether.  My only goal is to \emph{help} you.''



``Help me?''  I asked.



``There's two very different paths we could take.  The first is simple.  I'd act as your therapist.  I would be an objective ear, and I could equip you with tools to handle things like stress, anger, or anything else that concerned you.  Anything you said would be entirely confidential, and I would decline to comment when the time came for your placement in the Wards, so as to preserve that confidentiality.''



``Isn't that damning?'' I asked.  ``If you don't have anything good to say, they'll naturally assume you know bad things.''



``I don't think so,'' she said.  ``I've had upstanding heroes choose to exercise their right to confidentiality.  If we started off by establishing this as therapy right off the bat, there would be enough forewarning that it wouldn't reflect badly on you.''



``Okay,'' I said.



``The second route would involve me not being your therapist, but your \emph{advocate}.  We'd set you up with someone else as a therapist, and I'd focus on serving as a middleman, in working with the PRT, Protectorate, the Wards and the warden at Gardener.  I could, for example, talk to the warden about you getting a chance to run in the mornings, testifying that it'd be a good, healthy release.  When the time came for you to be placed with the Wards, I'd testify with all of the good and the bad, from what we've talked about here.''



``That makes a lot of sense,'' I said.



``There's a middle ground between the two options,'' she said, ``I could certainly be an advocate for you if you were coming to me for therapy, or offer you a listening ear if you were coming to me for advocacy.''



``With the knowledge that anything I said could be used against me, in that case.''



She nodded.  ``So long as you know.''



``I could really use an advocate,'' I sighed.



I thought of how she'd composed herself, pulling herself together.  It struck a chord.



``But I think I'd rather have you for a therapist.''



``Thank you,'' she said.  ``And I respect that you're willing to ask for help.  That takes a kind of strength.''



I shrugged.



``Is there any particular place you'd like to start?''  she asked.  ``We already touched on bureaucracy, you seemed a touch bewildered that I would respect you.''



She paused, as if waiting for me to chime in.



``There's other things, but it's hard to articulate them.''



``Give it a try.  It's sometimes easiest if you start with the underlying emotion.  \emph{I feel, }followed by the emotion, then talk about why.''



I nodded.  ``I feel\ldots anxious, because I'm worried I'm not a very good hero.''



``Assuming it isn't inexperience, is that so terrible?  Being less than stellar?''



``Doesn't it say something ugly about me, if I make a pretty excellent villain and a crappy hero?''



``Maybe it says something about your power, or it's simply past experience.  I stress, you are \emph{new} at this.''



``When I was \emph{new} at being a villain I took on established heroes and robbed a bank, walking away with a small fortune.''



``You had a team with you.''



``I felt a hell of a lot more effective, when I count everything that's happened without teammates at my back.  I dunno.''



``So you're restless and anxious-''



``And genuinely afraid,'' I said.  I sighed.  ``I feel\ldots \emph{afraid}, because I'm starting to think that maybe my power isn't entirely under my control.  There's a monster taking up real estate in my brain, deciding to use my power when I don't want to, and I'm pretty sure it's been getting more effective over time.''



``Is this monster metaphorical?''



``That's a \emph{very} good question,'' I said.  I leaned on my knees and stared at my hands.  ``Is it just me?  Or is it my `passenger', some inscrutable life form from a parallel universe that decided to give me powers, currently helping me manage those powers so my brain doesn't overheat?  Or is there even a distinction?  Did my trigger event fuse us to the point that the line is blurred beyond recognition?''



``I can see where the idea would be frightening,'' she said.  ``I've heard of some of these things, though the particulars and names differed.  We don't know enough about them, about powers, even, and the unknown is daunting, especially when it affects you as deeply as your power seems to affect you.  This lack of control, it-''



``If I tell you I'm dangerous, that I'm going to hurt someone, intentionally or by accident, are you obligated to report it?''



``Yes, if the risk is grave.  Forgive me for asking, but \emph{are} you going to hurt someone?  Accidentally or otherwise?''



I shook my head.  ``No.  But it makes me wonder if something like that is a possibility.''



``I've worked with a lot of young parahumans who had uncontrollable powers.  There are options.''



``Like?''



``It depends on the form this lack of control takes.  Is it perpetual?  Does it hinge on you losing focus?  On your being tired?  Illness?  Anger?''



``I'm not entirely sure.  Sometimes when I've been knocked out, I've found that my power keeps going without my instruction.  It's not \emph{brilliant}, it makes mistakes, and the logic isn't always there, but I've had my power keep working when I was unconscious, after a concussion, and when a cape used their power to wipe away my volition.  When I was tranquilized, after setting my bugs on Director Tagg, they apparently kept going after him.''



``Let's start with the fundamentals, then.  I almost always recommend relaxation exercises and meditation to my patients with control issues.  There's almost always a degree of improvement.  The next trick is to find a way to track this.''



``I'm getting a new costume.  Maybe a camera?  The most recent time I noticed it was when I was with Glenn Chambers, he showed me a video, and I saw myself using tricks I'd never taught myself.''



``Perhaps a camera, then.  Is it reassuring, to know that there are answers?''



``I'll be reassured when I see improvement,'' I said.  ``No offense.''



``None taken.  But you raised two problems.  Your lack of confidence about being a hero.  That's more immediate, if less ominous?''



``It's pretty ominous, honestly,'' I said.  ``I staked a lot on this.''



``You have options in mind, am I right?  You said that you were suggesting a new costume and new equipment.''



``But that doesn't fix things if I'm a round peg in a square hole.  I've thought about compromises, stuff beyond the gear and costumes, but I feel like I'm almost betraying myself.  The me that spent three months after getting powers, with the idea that I'd be a hero.  I had all of this idealism, all of these ideas of how I'd help, big and small, and I wind up doing more good as a notorious villain than as a hero.''



Jessica Yamada made a note on her pad of paper, then set it on the small table to her right.  She glanced at the window, then at me, ``Are you still restless?''



``\emph{All the time},'' I said.



``Want to go for a walk?''



``Hell yeah.  Am I allowed?''



``I'll need to make a few phone calls.''



\blacksquare



Middle schoolers swarmed around a very unhappy looking team of Wards, pushing, jostling, calling out, reaching to touch armor and costumes.  The overcast sky was only just clearing up, causing the colors in the park to be all the more vivid.



``\emph{Why}?'' I asked.



``Why are we here, or why is this happening?'' Mrs. Yamada asked me.



``Yes.''



``This is happening because of you, in a roundabout way,'' Mrs. Yamada said.  ``When your secret identity was revealed, it didn't take the media very long to discover that you'd been bullied in high school.''



``Oh hell no,'' I muttered.



``People asked why more hadn't been done to reach out to you and individuals like you.  This was the response.''



``I'm not sure this is a good thing,'' I said.  ``These assemblies and events were always atrocious, with really bad speeches.''



``I saw enough of them when I was in high school, I know.  But superheroes have the `wow' factor, at least.''



I looked at the very uncomfortable Boston Wards.  They \emph{had} enthralled the kids, but they couldn't \emph{do }anything with them, with the crush of bodies.  The teachers seemed to be enjoying the break, sitting on the far end of the field, in the shade.



``Want to wow them, too?''



I glanced at her.



``Not a fight, but a chance to be heroic.  The PR that's been forced on your head won't be a handicap here,'' Mrs. Yamada said.  ``And maybe it will help you feel a little more human, at a time when you're worried about the monster inside you.''



``A little heavy-handed,'' I commented.



``A \emph{lot} heavy-handed,'' she said, smiling.  ``But it's a chance to be outside, instead of cooped up in yet another room, without worrying your life's at risk.''



``I'll take it,'' I said.  ``Thanks.''



I ventured into the fray.



A hundred kids, all probably from one school.  I almost would have rather been up against Bambina.



I called on every butterfly in the area, across the whole park.  It took nearly a minute before they were gathered.  I sent them into the crowd, flying over and around the mass of kids.  Some of them screamed, others ducked, covering their heads.



Not quite the delight I'd hoped for.



Was this another point where I was underestimating what the effect of the swarm was, or were the kids just overreacting?  It was only five or six hundred butterflies.



``Whoever catches the most wins!'' I called out.  ``Go!''



The kids stared at me.  Some were still reacting from the rush of butterflies.



``Go!'' I said.  ``There's a prize!  A good one!''



They scattered.



Butterflies wove in around one another, around trees, out of reach and over heads, between legs and under tables.  I watched the crowd, got the kids to bump into one another, gathered them into clusters where I had ten or twenty students running after one group of butterflies, conserving effort and increasing the confusion when two groups ran into one another.



When the mass of kids had burned off their initial energy, I joined the Wards, still controlling the butterflies.



``Thanks,'' said one heroine in pale blue.



``A bit much?''  I asked.



A guy with a fox mask said, ``You can't really interact with them when there's this many.  There's no point.''



``Good memories,'' I said.  ``Better than nothing.''



``But not great,'' fox-mask said.  ``Good memories aren't exactly why we're here.  Somewhere in that group, there's kids who could be the next wave of capes.''



I watched the kids run.  They'd succeeded in surrounding one group of butterflies, and some had taken off rain jackets to form improvised butterfly nets.



That kind of organization deserved a reward.  On the flip side of things, they were liable to murder one another over a handful of butterflies.  Competition trumped reason.



Making the butterflies simply rise into the air was too easy, and there were some kids who were sitting on each other's shoulders, to get more height in anticipation of the tactic.



I swept up butterflies with dragonflies, carrying them out of reach, through the crowd.



Some of the kids rushed up to me, red in the face with exertion.



``You're cheating!''



``Not fair!''



``I used to be a supervillain,'' I said.  ``I'm allowed to be a jerk.  Go!  You two are in second place, but you're falling behind while you complain.''



They gave me death glares, then ran off.



I focused on my power.  The power I wasn't entirely sure I could trust anymore, and I identified the stragglers.  The ones without a group.  The ones who weren't participating, or who weren't able to maneuver around the crowd, solitary in the midst of groups of friends.



``Can you guys do me a favor?'' I glanced at fox-mask.



He nodded.



A few quick instructions, and the Boston Wards were mobilized, tapping on shoulders, saying hi to each of the ones I'd identified.



We gathered at the picnic tables.



``What's the point of this?'' one kid asked, a twelve or thirteen year old with hair draped over half his face.  \emph{Never understood that hairstyle}.



``A break can be nice,'' I said.  ``Whether it's from school or saving the world.''



``Inviting us here, I mean.''



``You want the cheesy answer or the real one?''



``Cheesy,'' one heavyset girl said, with just a touch of snark.



``Cheesy answer is you didn't seem interested in going squee over these guys, you didn't feel like chasing butterflies, so I figured I'd invite you to hang.''



``It's so fake, ridiculous,'' she said.



``It is,'' I said.  ``Fake can be good.  Reality sucks sometimes.''



``What's the \emph{real} answer?'' the guy with hair over his face asked me.



``The real answer is that this whole thing is a ploy by the good guys,'' I said.



He rolled his eyes.



``They want to get on your good side, just in case you get powers,'' I said.



He rolled his eyes again.



``Powers?'' another kid asked.  He was shorter than all the others, and his eyes were disproportionately large for his face.



``Powers,'' I said.  ``And you guys, I'm thinking, are among the most likely to get them.''



I was getting funny looks.



``Do you know what trigger events are?'' I asked.



He shook his head.



``Um,'' one of the boy heroes said, ``Not sure this is approved.''



I cocked my head, turning to the kid with the hair in his face, ``See?  It's a ploy.  Big secrets.''



``Not \emph{that} big,'' Fox-mask said.



``I didn't find out about trigger events until months after I'd had mine,'' I said.  ``It's how you get superpowers.''



Okay, that had their attention.  Twelve or thirteen pairs of eyes were fixed on me.



``It takes something pretty lousy to happen to you,'' I said.  ``You get attacked, or you get hurt, or someone attacks someone or something you really care about, and you have nowhere else to turn, and you get powers.''



``It doesn't work if you force it,'' Mrs. Yamada said, approaching the table, ``so don't try.''



``Right,'' I said, though I was digesting a tidbit of information I hadn't had.



``Why are we going to get powers when they won't?'' another kid in our cluster asked me.



``Because you were alone.  It's a bit of a trend, I think, one I've noticed.  I've seen a lot of powers, and I've seen a lot of people with powers who had similar things wrong with them.  Labyrinth, Bakuda, Night, Fog, Mannequin, Siberian, Lung, August Prince\ldots again and again, it's their ability to \emph{communicate} that's missing, either because of their powers or because they chose to hide or mask their voices.  I was thinking about it, and I think we parahumans tend to be loners by nature.''



\emph{Which might explain why we struggle so much as a community}.



``So you're here to make nice, just in case?'' the boy with hair in his face asked me.



``That's the gist of it.  I think the PRT's cunning plan is to get you on board before you get powers.''



``As if,'' the boy retorted.



``Hey,'' fox-mask said, ``Not cool.  We're trying to be nice here.''



I could see a scowl, the glance away on the kid's face.  I was put in mind of Regent for an instant.  A similar personality?



``No, let's be fair,'' I said.  ``Being a villain's an option.''



``You did\emph{ not }say that,'' Fox-mask said, incredulous, ``It's not an option at all.''



The girl in blue looked at Mrs. Yamada, ``Ex-villain's corrupting the kids, and you're not stopping her?''



Mrs. Yamada was frowning at me.



``I'm going somewhere with this, honest,'' I said.



``If you're sure,'' she said.  ``I can stop you at any time.''



``You can.''



I looked at the gathered kids.  A few of the less successful butterfly catchers had drifted away and approached.



``I always hated the speeches when I was in school, the preaching in auditoriums, the one-note message.  Stuff like saying \emph{drugs are bad}.  It's \emph{wrong}.  Drugs are fantastic.''



``Um,'' Fox-mask said.



Mrs. Yamada was glaring at me, but she hadn't interrupted.



``People wouldn't do them if they weren't.  They make you feel good, make your day brighter, give you energy-''



``Weaver,'' Mrs. Yamada cut in.



``-until they don't,'' I said.  ``People hear the message that drugs are bad, that they'll ruin your life if you do them once.  And then you find out that isn't exactly true because your friends did it and turned out okay, or you wind up trying something and you're fine.  So you try them, try them again.  It isn't a mind-shattering moment of horrible when you try that first drug.  Or so I hear.  It's subtle, it creeps up on you, and you never really get a good, convincing reason to stop before it ruins your life beyond comprehension.  I never went down that road, but I knew a fair number of people who did.  People who worked for me, when I was a supervillain.''



I had their attention now, at least.



This was probably going to hit the news as something like, `Ex-supervillain Wards member recommends drugs to kids'.  Whatever.



Maybe I'd get a shit placement in the Wards, but I felt more like the Weaver I wanted to be.



``It's the same, being a villain.  I went there, I did that for a few months.  Risked my life, hurt people, made an \emph{incredible} amount of money, but I look back, and it wasn't worth it.  I value the people I got to know and love far more than I do the money, the power, the fame.  They're the only thing I regret leaving behind.''



``How much money?'' the heavy little girl asked, grinning.



``You're missing the point,'' Fox-mask said.



``Fifteen or twenty million,'' I said, ignoring him.



``Shhh-ugar,'' one of the heroes muttered, just behind me, deciding on a new word midway through.



``That's \emph{so} worth it,'' a kid said.



``I think this is bordering on counterintuitive,'' Mrs. Yamada said.



``Do you have a piece of paper?'' I asked.



She only frowned at me.



One of the young heroes, a boy with goggles, handed me a pad of paper.



``Pen?''



He handed me a pen.



``What's your name?'' I asked the boy with hair in his face.



``Ned.''



I wrote it down.  ``Ned.  And you?''



I got the names of all of the kids I'd picked out.  The stragglers.  \emph{Maggie, Bowden, Ryan, Lucas, Jacob, Sophie}\ldots the list went on.  Fifteen kids in all.



I ripped off the sheet, then tore another sheet into squares.  ``More pens?''



The goggle-guy handed me a handful of pens.



``Each of you write down the most horrible thing you can think of, that you can \emph{reasonably} expect to happen to you in the next few years.  No need to get too complicated.  Think of something horrible that would give you a trigger event.  Write it down.''



I waited while each of the kids wrote something down.  Other kids were gathering now, but they'd be bystanders.  It was the stragglers who were the focus now.



``Hand your sheet to the person to your left.  Boston Wards, help me on this score.  We're going to make up powers that sort of fit the trigger events, in a vague way.  No need to be specific.''



``If it helps,'' Mrs. Yamada said, ``More mental powers for mental stress, physical powers for physical stress.''



``She's the expert,'' I said.  ``Let's go.''



``I want to pick my own power,'' Ned said.



``Too bad.  You don't get to in real life,'' I said.  ``You think I wanted bug powers?''



By the time we'd finished, more of the butterfly catchers had come back.  They were watching, now.



``Ned gets the ability to fly.''  I'd left him for last. ``And some sort of ranged attack.  Kind of like Legend.''



``Sweet.''



``But no power is really that simple.  So\ldots you fly by \emph{blowing}.  Like a balloon with the end untied, only with more control.  You attack by blowing too.''



``No!  That sucks!''



``Too bad,'' I said.  ``It's not all fun and games.  What was your trigger event, Maggie?''



The heavyset girl frowned, blushing a little.  ``Um.  Someone chopped my wiener off.  How does that-''



``It doesn't matter,'' I said.  Someone hurt you badly, and you got a more physical power?''



``Reynard said I got super strength, and regeneration.''



She looked at Fox-mask.  I had his name now.



\emph{A little boring, whatever}.  ``Okay.  Now, on the back of the sheet, write down whether you're a hero or a villain.  Your choice.''



``This has got to be a trap,'' she said, ``So hero.''



``Okay,'' I said.  ``And do you join the Wards, or no?''



``Join us,'' Reynard whispered, urging her.



``Kind of seems like a pain.''



Reynard groaned.  ``I'm wounded!''



``So you're on your own, or you join another group?''



``Another group.''



``Okay.  And\ldots Bowden?''



The kid smirked.  ``Screw that.  I want fifteen million dollars.  Villain.''



``Okay.  Ryan?''



We went around the circle, until everyone had their affiliation.



``I don't suppose you'd have any dice?'' I asked the Wards.



The goggle-hero handed me a handful of dice.



``Oh shit,'' Ned said, ``You conned us into playing dungeons and dragons!''



``Nothing so complicated,'' I said.  ``Roll, Ned.  A three is bad luck about your powers, a two is bad luck about your life as a cape, and a \emph{one} is really bad luck.''



He rolled.  A three.



``Aw, what?  No!''



``Okay,'' I said.  ``Your powers came with a drawback.''



``I blow \emph{air!}  I already got screwed.''



``Your power came with the ability to understand air currents, which you need to fly,'' I said.  ``But they erased something else.  Your sense of direction is gone, unless you're using it to fly.  Wherever you go, you get lost.  It's bad enough that you can't do anything on your own.  Unless someone here asks you to join their team, your life is ruined.''



``\emph{What}?''  He asked.  He glowered.  ``Fuck you.''



``Language,'' Fox-mask warned.



``It happens,'' I told the kid.  ``Let's hope others have more luck.''



We went around the table, there were a few more with bad luck.  I found it interesting when the Boston Wards volunteered penalties.  One involved a trigger event so public that a kid had to abandon the idea of a secret identity.  Another was traumatized by theirs, and wouldn't get a good night's sleep for ten years.



``Now let's talk about what you do with your careers,'' I said.  ``Ned?  You found a team, and your power's pretty good, so let's say you win a fight against the heroes on a two or better.''



He rolled, ``Six!''



``Now you fight other villains, who want to steal the money you just got.  Roll.''



``I'm a bad guy, I'm not fighting them!''



``Bad guys fight villains \emph{and} heroes,'' I said.  ``But you can give up the money if you want to run.''



He scowled, shaking his hand in anticipation of rolling, dragging it on far too long.



``And because bad guys don't always play fair, these guys kill you if you roll a one, and they win on a two,'' I added.



He rolled.  A two.



``Money gone, you're hurt, embarrassed, but still alive.  Maggie, your turn.''



The exercise continued.  Once we had a general system in place, crude rules or no, the Boston heroes took up the job, until each of us had three `capes' and a small crowd of spectators.



``I'm not sure I get the point,'' Maggie said, after a few rounds.  She looked a little nervous with a crowd looking over her shoulder.



``Okay,'' I said, clapping my hands.  ``Villains, raise your hands.''



They did.



``If you're dead, maimed or in jail, lower your hands.''



More than half of them did.



``Heroes, raise your hands if you're okay.''



Most of the other kids raised their hands.



``Sophie chose to be a rogue,'' Fox-mask said, ``She's been in one fight, but she came out okay.''



``You're screwing the villains,'' Ned said.  ``It's not \emph{really} one fight after another.''



I opened my mouth to speak, but was interrupted.



``Being a villain is hard,'' Mrs. Yamada said.  Odd as it was, she seemed to have a measure of authority I didn't, here.  Weird, that the kids would listen to her because she was an adult, and not someone who'd actually been in the thick of it.



Weird and frustrating.



``One in twenty might make it in the long run,'' I said.  ``If they're lucky, if they're good, if they have friends they can count on.''



``Pat yourself on the back a little more,'' Reynard said, a little sarcastic.  The girl in blue elbowed him.



I made sure to look each of the participants in the eye as I spoke, ``I wasn't satisfied doing what I was doing, as a villain.  I switched sides by choice.  Think about that.  Even after all of that, after everything I had, even though I felt pretty good, spending all of that money on helping people in my neighborhood, being front page news, I gave it up.''



I knew it wasn't time for it, that I should let that sink in, but people were talking more in the back of the crowd, jostling or getting restless.



``So let's say there's an endbringer attack,'' I said.  ``Time to decide.  Do you volunteer?''



Nobody moved.



``We need volunteers, or it's over,'' I said.  ``Hero or villain.''



Maggie put her hand up.



``One,'' I said.  ``Not enough.''



Others raised their hands in turn.  Five volunteers out of the eight who were still in the game.  Ned was among them.



``Roll,'' I said.  I handed over the dice, ``One in four chance you die.''



The kids rolled, one by one.



Three dead.



``You rigged the system,'' Ned said, a little petulant.



``I'm being a little harsh,'' I said, ``But this is it.  It sounds dumb, but being a cape means beating the odds, again and again.  If you're a villain?  The reward is pretty damn good, but the risk is bigger.  You saw how few villains actually survived intact.  Even then, a lot of them lost their money, or got hurt.''



I glanced around the group.  ``That's my pitch.  Take it from someone who's been on both sides.  Being on the side of good?  It's safer, a hell of a lot smarter.  Know that there's always going to be someone out there that's stronger, and-''



The ringing of phones interrupted me.  Multiple phones, all at once, both the Wards and Mrs. Yamada.



A sick feeling welled in my gut.  The Wards looked at their phones.  Mrs. Yamada was the only one to raise hers to her ear.  I closed my eyes.



``Yes,'' Mrs. Yamada said.  ``You're coming here?  Okay.  Yes.  Of course.  The Boston Wards are here.  Yes.''



I felt like my chest was clenching around my heart.  The kids had fallen silent.



``Weaver,'' Mrs. Yamada said.



My voice was quiet, ``I'm not ready.  My new stuff, it's not prepared.''



``Defiant says he has your old costume, he can spray it white, if you want, swap out the lenses.  It won't be pretty, but it'll be better than what they gave you.''



I opened my eyes.  The kids were wide eyed.



``Which one is it?''  I asked her.



``Behemoth.  Seismic activity building in New Delhi.  He hasn't appeared yet.''



I nodded.



``You don't have to go,'' she said.



I shook my head.  I thought of the Undersiders.  ``I'll go.  Have to.''



``Can I hitch a ride?'' Reynard asked.  ``At least to the HQ?''



I nodded, glad for the solidarity.  I wasn't in this alone.  ``Probably.''



I looked at the Wards, could see how some were standing taller, grim, fatalistic, but confident in their own way.  Others averted their eyes.  Shame, that they weren't coming.



``Hey,'' Ned said.



I glanced at him.



``Is it really a one in four chance?'' he asked.



``Those are the numbers they gave me when I fought Leviathan,'' I said.  ``They probably won't be so generous this time around.''



``They call him the herokiller,'' Reynard added.



That thought hadn't even crossed my mind.  \emph{We're not ready.  None of us.  We're still reeling from Echidna, from Alexandria.}



The kids who were still in the field fled as three Dragon suits set down, crossing the park to rejoin the teachers who'd been sitting in the shade.  Doors opened and ramps lowered to welcome us into the dark interiors.



Defiant and Dragon were inside the Pendragon, waiting for me, Defiant carrying my Skitter costume, Dragon holding a new back compartment, wings extended, two mechanical limbs sticking out each side.



It wasn't everything I'd asked for, but it was \emph{something}.



I glanced back at the kids. The ones who hadn't cleared the way for the crafts to land in the park were still at the tables, along with one or two Wards who apparently weren't coming.



``Still owe you that prize,'' I said.  My voice sounded funny.  ``Was going to con Defiant here into giving you a ride.''



``Doesn't matter,'' a girl said.  She had the most butterflies.  ``Really.''



I nodded.



It had meant something to me after all, getting the chance to do this.  I met Mrs. Yamada's eyes, nodded.



She nodded back.



Gathering the Skitter costume and the lightweight jetpack into my arms, I watched the kids as the doors slid closed.



None of them wished us luck.



Maybe we didn't need any further reminders about our chances.





