





The waiting was the worst part.



My restlessness was cranked up to eleven, cooped up in the craft with Defiant and Dragon, waiting to cross half the world.  Dragon was focused on piloting the craft, unable to speak, in any event.  Defiant was busy communicating, which translated to being inaudible as he kept the vents of his mask closed.  From the images on the monitor, he was clearly tracking who was coming, our forces, the Endbringer and the high-risk areas.



I watched for a time, saw the cape count rise.  A screen filled with lines of text, noting the hero teams who had committed to the fight, numbers beside them to tally the total numbers.



For every group that joined, I felt myself growing a touch more nervous.  More participants in the fight was a good thing, but\ldots so many small teams.  I couldn't read half of the names of the groups on the list, but there was nothing to suggest it was organized.



I shifted my weight, sat, stood, stretched.



\emph{Agony}.



Being in a prison, I didn't have the luxury of a full wardrobe, certainly not the bike shorts and tank top I tended to wear beneath my costume.  I had only underwear, and I needed to change into the new costume.  I \emph{could} have waited, but I wanted to hit the ground running.



Worse, the boxes with my butterflies within were in one of the crafts that followed just behind us, carrying a full contingent of capes.



But Defiant was engrossed in the monitors, and that left me debating the merits of modesty over being ready.



I stripped down, pulling on my old costume.  They'd said something about painting it, but I wasn't sure I wanted to wait for that.  I left the major armor components off.



The pack they'd given me, it was the wrong color to match with the armor.  I'd be sacrificing the ability to keep things inside my utility compartment, but I suspected this would make up for that.   There were built-in wings that folded at a juncture, like dragonfly wings with joints, and there were the `arms'.  The controls seemed to be worked into gloves I was supposed to wear beneath my costume.



I found that there was a hatch, but it was small, barely larger than my hand, and the space was shallow.  I sent bugs inside to explore, and found a series of fine switches.



``Redundant controls,'' Defiant said.



I looked up.  He'd turned away from the monitors.



``If your glove gets damaged, you've got the controls built into the pack itself.  If the pack gets damaged, you have the gloves.  If both are damaged, you're not likely to be in a state to fly.  It might take getting used to, but this will give you the ability to move faster if you need it, and it's very possible you'll need it this afternoon.''



``You built it so fast.  I wasn't with Mrs. Yamada for even two hours, and you put this together?''



``It's made using components and technology we already have.  Four antigravity panels, like those Kid Win had in his hoverboard,'' Defiant said, angling his hand to indicate the general placement.  One at the very bottom, one above that, facing more \emph{back} than \emph{down}, and two more at angles on either side.



``Okay,'' I said.



``That gives you lift, the ability to offset gravity or momentum in a given direction, but the acceleration is low.  Expect zero to thirty miles an hour over eight seconds.  It won't carry you out of the way of trouble, understand?  It won't stop you if you're moving at terminal velocity, unless you're falling a \emph{long} way.''



I nodded.



``The wings are a modification of technology that was confiscated from a cape called Stinger.  Missile themed, not wasps and bees.  They've got a venting-exhaust system we repurposed.  It toggles between using either antigravity or propulsion.  They should give you an easier time orienting yourself, or more speed pushing yourself in a particular direction, but not both at the same time.   While the wings are intact, you should be able to manage zero to forty-five in about three and a half seconds.  That ends if the wings break, and they aren't made to be durable.''



I nodded.  ``It won't let me flit around the battlefield, but it'll give me some vertical movement?''



``Yes.''



He continued, indicating lines with his finger.  ``We built nineteen tracks into the device, that you'll be able to control with the bugs you direct into the interior.  One for the on-off switch, doubling as an override for the glove handling, four for antigravity panels, eight for the arms, six for the wings.  You're sure you can handle all that?''



``Multitasking is a strength of mine,'' I said.  ``If it's anything like controlling Atlas, it'll become almost subconscious.''



``I hope so.  You'll want to learn with both the glove and the insect control.  There's also limitations on energy and fuel, for the antigravity and propulsion, but not so limited that you'll run out by the end of the day.  You have time to review the documentation Dragon put together.  Pay attention to the particulars of the flight pack's vulnerability to electromagnetic radiation.  While the wings are deployed, one good hit will scramble it and render you flightless.  While the wings are withdrawn and the casing closed, it should be shielded against all reasonable EM sources.''



``I'll have to stay close to the ground then, in case it gets scrambled.''



``For now.''



``Can I practice?'' I asked.  ``Not flying, but the arms, and moving the individual components\ldots''



``The arms aren't done.  Keep them out of the way for now.  Until I figure out a way to approach the internal design, they'll have about as much strength as a newborn baby.''



I nodded.  ``I really appreciate this, anyways.  You two went above and beyond the call of duty.''



``It's not customary for tinkers to design things for teammates.  If they do, it's on a relatively small scale, simple.  Kid Win making Gallant's armor, for example.  Any device requires a great deal of upkeep.  Time is spent tuning, calibrating, repairing and identifying problems.  Each device created is something the tinker then has to take time to maintain, and mass production means the tinker becomes tech support more than an innovator.  Dragon and I don't sleep, or sleep very little, but even for us, it isn't effective.  Far better to invest our time into the artificial intelligences and the ships.''



``But you're doing this for me.''



``We, \emph{I in particular}, wronged you,'' Defiant said.  ``I know that even now, we're not fully on the same page, but I now believe you did start out wanting to be a hero, and I may have played a part in your drift from that path.  I've put myself on the line to recommend you to the Wards, and I'll dedicate the time and equipment necessary to get you on track.''



``Thank you,'' I said.  ``Really.  Thank you.''



``If you don't mind,'' he said.  ``I--''



He paused, glancing at Dragon.  Then he continued, ``I'm working on being more humble, but I think I will always have a certain measure of pride and an excess of focus, to the point that I lose sight of the periphery of things.  I'll forgive your past transgressions if you look past mine, and if there's any disparity in the two, I'll make it up for you with this.''  He lowered his head to indicate the flight pack.  ``And I'd ask you to spare my ego the reminder by accepting this without thanks.''



``I've worked with Rachel, with Bitch, I think I can do that much,'' I said.



``When this is over, today, if we're all still alive, I will maintain two of these packs for you, and you can switch to the spare if one needs repairing or recharging.  Some of it's of Dragon's design, but the maintenance will be left to me.  If you have questions, I'll answer them,'' he said.



And the latter half of the statement was left unsaid.  \emph{But}\emph{let's not talk of this any further, unless it's about the technical aspects of the device}.



He had already turned back to the monitor.  There were three screens filled with columns noting the various teams who were showing up.



``How long until we arrive?''  I ventured.



``Forty-five minutes.''



I nodded.  ``We're going to show up late, aren't we?''



``Inevitable.  Dragon already has had every combat-ready craft on standby in eastern Europe for a week now.  They and the local forces will have to hold the fort until then.''



``Okay.''



``The computer opposite mine is available.  Dragon is pulling up the documentation on the flight device now, if you need something to occupy yourself.''



I glanced behind Defiant, noting the terminal and the stool that was built into the craft's cabin.  I took a seat, resting the pack on my right thigh.



Okay, so they'd found the time to pull together a flight pack with some antigravity and propulsion systems, I could believe that.  But the documentation?  Who had time to draw out 21 pages of notes on capabilities and limitations, on top of building the thing?



Especially when it was all drawings, rather than typed out words.



I wasn't about to complain, but it did leave me reconsidering what Dragon's specialty might be.  I'd thought I worked it out, but the speed with which she'd pulled this together\ldots



My bugs found the channels inside the suit, and I set about experimenting with it, working through the various steps for moving the wings and the individual limbs.  Each `track' inside the pack's interior was a narrow corridor with very sensitive switches along the interior, so that any movement of even something as diminutive as a ladybug was capable of pushing them.



The sensitivity would need to be calibrated at a later point.  As it stood, any jarring impact would briefly lock all of the inputs in place, so they wouldn't read the impact as contact from a bug and send the wrong signal.



I had to shrug out of the upper half of my costume to get the gloves on beneath my costume, but I managed to get everything set up.  There were too many straps and no room for them to slot beneath my costume, so I connected them over the costume's exterior, beneath the armor, and cinched every strap tight, doing up the metal clasps once everything was comfortably tight.



There were four `arms', each a little longer than my arms.  The control was a little simplistic, with only two switches for each limb.  I imagined it was similar to an artificial limb.  I folded them close to my body, so they hugged my lower ribs and the space just beneath my `breasts', and then left them be.



The wings were just as simplistic, but had three switches each.  Two to move and reorient the wings, with a third to switch between the antigrav vent and varying amounts of propulsion.  I didn't dare experiment with that in an enclosed space.



I read and reread the documentation ten times over, because there was precious little else to do.



``We're landing in a minute,'' Defiant announced.  ``Estimated eight minute wait before the last craft from North America arrive on site and a cape by the name of Silk Road deploys a corridor.''



I nodded.



``We picked up your old team,'' he said.  ``Sent a craft.''



I turned around, surprised.



``Stipulations of your membership in the Wards dictate that you aren't to extend contact to them.''



\emph{Oh.  Right.  Shitty.}



``Keeping in mind that there are likely going to be cameras and cell phones pointed at you throughout this incident,'' Defiant said, glancing at Dragon, ``You're free to do as you wish.  So long as you don't do anything troublesome on camera, I don't expect anyone will make an issue of it.  It might even help if you allow others to record you, so it's clear you aren't doing anything questionable.''



I glanced at him.



``Dragon's suggestion, not mine,'' he said.  ``But I don't object.''



``Thank you,'' I said, meaning it.



``Thank me by staying out of trouble,'' he said, brusque.  He glanced at Dragon, then back to me.  ``And you're welcome.''



\emph{She can communicate with him, but not with anyone else.  Why?}



I nodded.  ``Um.  You reminded me, when you said there'd be people getting camera footage of me.  Mrs. Yamada said I should start recording myself while I'm in the field.  I know we still have to talk about my costume, and it's too late to make any updates, but I wouldn't mind having it, especially for the next high-intensity situation.''



``We'll see,'' he said.



I nodded.



The craft set down, the doors opening.  My mouth dropped open in surprise as I took in the scene.



The area was a flat, open field with knee-high grass.  Settled on it were twenty of Dragon's ships, with two to sixteen capes to each.  People were stepping out, stretching, meeting others and talking.  Almost all of them were from the Protectorate and the Wards.  Others included Haven, a villain group I didn't recognize, and one of the corporate teams I'd seen before the Leviathan fight.



And the Undersiders.  I sensed them with the bugs in the field.



I felt a measure of hesitation.



\emph{Time to test out these wings}.



It wouldn't do to faceplant in front of all of these heroes.  I was tentative, as I sent a bug down a tight corridor with innumerable tiny switches.  Only one corridor, one switch.



A panel kicked to life, gentle.  I nearly tripped as I stepped forward and was lifted an inch or two higher off the ground than normal.



I sent the bug further down the corridor, directing more power to the panel, and I was no longer having an issue, because I was being lifted into the air.



I was starting to lose my balance, though, necessitating a drop in lift and some experimental firings of the left and right panels to keep myself upright.



I touched ground and extended the wings, activating the vents for the antigrav at the wing's tips.  It made for a sudden, lurching adjustment, nearly flipping me over to the ground.



Not wanting to waste too much time, I made a beeline for the Undersiders, experimenting as I went.  Rather than \emph{fly}, I used short bursts of the antigrav with kicks of my feet to get some air, landing on the noses and limbs of various Dragon-crafts, so I didn't have to walk around.



``There she is,'' Tattletale said, ``And she's flying.''



I settled on top of a head, swaying for a second as I touched ground and found my center of balance.  ``Floating, until I get more practice.''



``Close enough,'' she said.  She flashed a grin.  ``Fancy.''



They were all present, Parian included.  Accord, Citrine and the woman with the water powers were all present.  I couldn't recall her name.  Ligeia?  She had a costume, now.  Or an evening dress, rather, with a conch brooch and mask.



More than Parian, I was surprised that\emph{ Accord} had come.



Flechette, now Foil, stood off to one side.  She'd donned a black costume, which I was pretty sure was made of one of my failed attempts at a Tattletale costume, using asymmetrical belts, boots, armor and gloves to cover the areas where I'd tried to embellish.  Her mask was an opaque pane, like Clockblocker's, but black, with silver trim at the edges.



``You're wearing your old costume,'' Grue said, finally.



``Haven't had a chance to make a new one,'' I said.



``No kidding,'' Regent said, his tone dry, ``Too busy making license plates, dropping the soap\ldots''



``I can't believe you went and became a hero,'' Imp said.  ``What the fuck?  How the fuck do you off a major cape and get \emph{invited} to the Wards?''



``It's complicated,'' I said.



``Are you getting by?'' Grue asked.



``Not as well as I'd like,'' I said.  ``But surviving.  Are you guys okay, leaving your territory like this?''



``Hey now,'' Regent cut in.  He stabbed a finger at me.  ``Aren't you supposed to read us our rights before questioning us?''



Imp snorted.  Grue smacked Regent across the back of the head, a little harder than necessary.



``It's all good,'' Tattletale said.  She grinned, ``Booby traps, some misdirection, I figure we can afford to be gone for a day.  We can look forward to going back home to see some bruised egos.  Regent's dad among them.''



``You're being safe?'' I asked.  ``I mean, we've taken on some monsters, but this is Heartbreaker, and the repercussions of a lost fight are kind of, well, permanent.  There's no undoing his power.''



``Like I said, it's all good.''  Tattletale shrugged.



``You with a team?'' Grue asked, ``Or with us?''



``No idea.  As far as I know, I'm independent,'' I said.  ``I'm not sure what that means, yet, but way I figure it, I'm going to do whatever works best in the moment.''



``Isn't that how you wound up with us in the first place?'' Tattletale asked.



I didn't have an answer to that, so I shrugged.  My eyes followed Foil as she walked over to talk to Jouster.  He handed her an arbalest, and a quiver of needle-like bolts.



When she took the quiver, he gripped her wrist, speaking something in a low volume.  She nodded as she replied, saying something I couldn't make out, and he let her go.



Wordless, they parted, him rejoining his team, Foil moving to Parian's side.



I wanted to say something about that, but what?  I didn't get the vibe she was a double agent, but I imagined there was something more to that.



I turned my attention back to the Undersiders, and my eyes moved to Rachel.  She was sitting on the ramp at the back of a craft, her dogs clustered around her.  She was stroking Bastard, using her fingernails to get in deeper than the base layer of fur.



Finally a chance to talk, and nothing to say.  The silence hurt me more than any accusations or insults.



``I don't know how to say this gracefully,'' I said.  I paused, noting the presence of a hero nearby who'd raised a camera towards me.  Whatever, I'd say it anyways.  ``But you guys mean a lot to me.  I'm sorry I didn't say it before, but I couldn't without letting on that something was going on.  You're my family, in a way.  As lame as it might be, I love you guys.''



My head turned from Grue to Rachel to Tattletale as I said it.



``Gaaaaaaayyyyyyy,'' Imp drew out the word.  Parian and Foil gave her an annoyed look.



I smiled a little, despite myself.  ``Fuck off.''



``Are you \emph{trying} to get someone killed?'' Regent asked.  ``That's totally a death sentence, telling someone you love them, tying up loose ends.''



``She'd be getting \emph{herself} killed, going by the rules,'' Tattletale said.



``Don't say that,'' Grue said, his voice quiet.



With a touch more seriousness, Tattletale said, ``No dying, okay, Skitter?''



``Weaver,'' I corrected.



``Skitter,'' she said.  ``Here, today, you're Skitter.  Consider it a good luck charm.  And \emph{no dying}.  I'll say it as many times as it takes, until it gets through to you.''



I shook my head a little.  ``No dying.  That goes both ways.''



``Way I see it,'' Imp said, ``She's gone soft.  Real quick, too, getting affectionate, lovey-dovey.''



``Alternate costume, too,'' Regent said, ``White, light gray, baby blue\ldots''



``Electric blue,'' I said.  I was smiling now.  I used the flight-pack to slow my descent as I hopped down from the head of the craft.  I pitched my voice lower so I wouldn't be overheard, and poked Regent in the chest.  ``Fuck you guys.  I'm as badass as ever.  Recommending drugs to kids, strangling a ten year old, forcing bugs down my allies' throats\ldots''



``Killing Alexandria,'' Regent said.



``Mm,'' I said, and I could feel my heart plummet into my stomach.  All at once, I was left wondering just how many capes here were secretly blaming me.



``Asshole,'' Tattletale told Regent.



I folded my arms, feeling a chill, the summer warmth notwithstanding.  ``We may pay for that today.''



``I think we're fucked in general,'' Tattletale said.  ``But no sweat.  We'll--''



She snapped her head around.  There was an uncharacteristic emotion as she swore under her breath.  ``\emph{Fuck}.  He's up.''



A second later, the ships each spoke in their identical voices, out of sync not because of any flaw in Dragon's program, but due to their positions across the field, and the delay of sound traveling, a chorus, ``\emph{Behemoth has surfaced.  Return to your craft as soon as possible.  Supplies will be provided while we are en route.  Individuals on the ground may or may not be left behind.}''



``See you on the battlefield,'' Grue said.



``See you,'' I answered.  I felt a tug of worry.  I had almost hoped he'd sit this one out.  He didn't tend to do well when it came to facing down the real monsters.



I bit my tongue and started up the flight pack.



``Don't hold back \emph{now},'' Regent said.  I could see that he was watching the guy who was still training his camera phone on me.  Regent turned back to me and extended his arms, injecting fake emotion into his voice, ``You know we love you too!''



I kicked off, just barely floating out of reach as he tried to fold me into a hug.  ``Jackass.''



He was back to his casual, detached attitude in an instant, showing just a touch of swagger as he stepped back to rejoin the others.  He gave me a sloppy mock salute.  I shifted my ascent and set foot on the head of the craft that had been behind me.



``Just remember,'' Tattletale called out, ``You're officially Skitter today.  Don't be a hero.  No point to all this shit if you do something brave and get yourself killed.''



``Not sure about that,'' I said.  ``About being Skitter, not the getting killed bit.''



Heroes were rapidly retreating to the craft.  I didn't have long.  There was so much I wanted to say, but\ldots shit.



``Rachel,'' I said.



She glanced up at me, her eyes almost hidden behind her hair.  I could see the hurt in her expression, a raw feeling.



``The letter, it helped.  All of the letters meant a lot to me, except Imp's.  But yours especially.''



She grunted in acknowledgement, setting Bastard on the ground, then stood.



``And I'm probably going to get crucified for saying this, but I still consider you a friend.  Someday, after all of this has settled down, when you don't need to be a villain anymore to take care of your dogs, and I'm okay where I'm at, I want to hang out again.  Throw the balls for the dogs, clean up dog shit, go for walks.  Whatever works.''



``Saying shit like that, you're signing death warrants!'' Regent said, his hands to the side of his head.  ``Stop it, you lunatic!''



I shook my head, then turned and took flight.



All around me, doors were shutting.  If it weren't for my bug sense, I might have lost track of where Defiant was.  So many Dragon-ships, no two quite the same.



I entered, and I could see Defiant standing in front of the monitors, his arms around Dragon's shoulders.  One of them must have acknowledged my presence, because the doors of the craft began shutting behind me as I made my way inside.



Odd as it was, I hadn't fully parsed that they were \emph{together} before now.



I approached, quiet, and watched as the drama on the monitors unfolded.  The bugs from the field followed me inside, clustering around me.



Behemoth, nearly fifty feet tall, was still standing in the midst of a collapsed building.  The structure had no doubt fallen on top of him as he emerged, and the debris was ablaze, casting his gray skin in hues of red and orange.  He didn't seem to care about the building.



Dragon's A.I. were already attacking him, each from the greatest distance possible.  The camera shook, out of sync with the timing of the strikes, as the vibrations took time to travel to the distant cameraman.



Heroes were fighting, contributing pitifully little to the assault.  They were too distant to make out.



``Locals?'' I asked.



Defiant turned, reacting as if he were surprised I was present.  ``Yes.  Don't ask me to pronounce their names.''



``\emph{S\textoverline{a}has\textoverline{i} P\textoverline{a}n\=ca},'' Dragon said.



I glanced at her in surprise.  ``You can talk, all of a sudden?''



There was a pause.  ``\ldots{}Little.''



``She felt she needed to be able to communicate,'' Defiant said.  To her, he said, ``And this is the last time we make a last-minute fix.''



``I'm sort of in the dark here,'' I said.



Defiant declined to fill me in, staring at the screen.  His voice was almost \emph{pained} as he muttered, ``They're too close.''



One Dragon suit was unleashing what looked like a freeze ray at the Endbringer, while another of the Dragon suits was turning a laser on the ground beneath Behemoth's broad feet.  It wasn't enough to take away his footing.  He set one `claw' -a growth of obsidian-like black shards- onto solid earth, then half-loped, half-hopped forward.  With his claws and feet now on firm ground, he leaped.  The shockwave of his departure toppled the slipshod buildings around him in his wake.



The landing as he arrived flattened \emph{another} set of buildings.  The heroes started to run.  They were too slow, when compared to the length of Behemoth's legs, the sheer power he was capable of putting into the simple act of walking.  One by one, they fell within his kill range.  Two were scorched from the inside, a brawny-looking cape seized up with smoke billowing from his corpse as he struck ground, his arms and limbs still twitching in death.



One managed to escape, taking flight.  He got a full four city blocks away before Behemoth reached out.  He was struck out of the air by a visible arc of lightning that extended from a claw's tip.



Four A.I. were continually bombarding him now, three using what looked to be freeze-rays.  The fourth alternated between destroying his footing and blasting burning buildings flat with some sort of concussive laser-drill, stifling the spread of the fires.  Heroes here and there contributed some inaccurate ranged fire, but seemed preoccupied with fleeing.



Behemoth hardly seemed to care about any of it.



Our ship lifted off.  Outside, the surroundings were taking on a rosy tint.  I could hear the cumulative thrum of the twenty-seven Dragon-craft's propulsion systems operating in unison.  My bugs could track them all, the late arrivals included.



There was a shudder, and the rosy tint of our surroundings intensified, filling the cabin.  We started to move, and it wasn't the ship moving us.  Dragon stepped out of Defiant's embrace to approach the ship controls.



An instant later, the propulsion system kicked into motion, and we were moving far faster than before.  The shuddering of the cabin was so intense I had to sit down.



``India's capes fall into two categories,'' Defiant said, not taking his eyes off the screen.  He had to raise his voice to be heard over the movement of the craft.  ``They term their capes `hot' and `cold', with very strict rules on who falls into a category.  Walk between the two groups, you get the worst of both.  Hot, it's about flash, color, appeal, and engaging the public.  Villain or hero, they're cape celebrities.  Cold, it's\ldots bloodshed, violence, assassination and secrecy.  Capes of the underworld.  The public doesn't see or hear about the cold capes.  The media does not speak of them.''



On the screen, Behemoth wasn't even slowing down.  Another arc of lightning lanced across the cityscape, setting a dozen fires.  The houses looked shoddy, dirty, and were apparently very flammable.  The flames spread quickly, and plumes of smoke were streaming towards the overcast sky.



``The capes that are getting killed, they're--''



``\emph{Garama},'' Dragon said.  ``\ldots{}Hot.''



``We need the ones with killer instinct,'' Defiant said.  ``The ones who fight for real, not for play.  The cold capes.''



``\emph{Thanda},'' Dragon supplied the translation.



``Question is whether the \emph{Thanda} think it's worth breaking the rules and emerging from the shadows,'' Defiant said.



``Did last\ldots  time,'' Dragon said, her words bearing an odd cadence.  She approached me, holding an armband and a silver packet.



I accepted them, turning both over in my hands.  ``Radiation pills?''



She nodded, holding up one finger.



``Take one?''



``Yes,'' she said.  ``Still.''



``Still?''  I asked.



But she just touched one side of my face.  One finger was under my chin, and I raised it, looking up at her, confused.



She let me go, leaving me momentarily confused.  I touched my face where she'd laid her hand and felt two bumps.



A camera?



``Dragon,'' Defiant said, before I could ask any questions.  ``Look.''



She approached his side, her arms wrapping around his armored left arm, metal scraping against metal.



``They're not supposed to be here,'' he commented, his voice low.



I turned my attention to the monitor.  ``Who aren't?''



``The Y\`{a}ngb\v{a}n.''



The focus was on a formation of capes.  They were lined up like musketeers, rank and file, each a set distance apart from the others.  The ones in front were kneeling, the ones behind standing.  Each wore a mask that covered their faces, flowing costumes with loose sleeves and pants, somewhere between a martial arts uniform and a military uniform, each crimson with a black design of horizontal and vertical lines at edges of the sleeves and pants.  There were nearly thirty of them.



All together, they directed lasers at him, aiming for his one red eye.  He blocked the concentrated laser-fire with one claw, and the flesh at the base of the obsidian claw began peeling away.



``Who are they?''



``The C.U.I.'s military parahumans.''



``Isn't the C.U.I. xenophobic?''



``Yes,'' Dragon said.  Her voice sounded funny.  It wasn't emotion, but something was somehow off about it.



``Excepting diplomatic functions, this is the first time in over a decade that any of the Y\`{a}ngb\v{a}n have set foot outside of China,'' Defiant said.  ``We've tried to arrange for their aid in the past, but relations between our side and theirs are sour.  For years, they've alleged that the PRT and the Protectorate are fundamentally corrupt, the source of the problems currently plaguing the world.''



``They were right,''  I said.



``Yes,'' Defiant said.  He didn't sound happy about the admission.



Behemoth slammed his claws together.  The Y\`{a}ngb\v{a}n responded by creating forcefields en-masse, one for every person, overlapping with those to either side of them.  The shockwave of the clap ripped through them, shattering the first two rows of forcefields and virtually \emph{liquefying }the unfortunate capes who no longer had protection.



The Y\`{a}ngb\v{a}n in the back rows were already dropping their forcefields, extending their hands forward, open palms aimed at their comrades.



The shockwave's effects reversed in an instant, and the injured were whole, holding the positions they'd been in an instant before.  Here and there, the reaction had been a fraction too slow, and the Y\`{a}ngb\v{a}n members were only reversed to the instant the shockwave made contact.  They were thrown back and caught by the ones in the back row, blood streaming from their eyes, noses and ears.  One was saved much too late, and the process of being liquefied was only repeated, splattering the Y\`{a}ngb\v{a}n soldier who'd failed to react in time to rescue him.



Behemoth unleashed a rolling tide of flame, and the remaining twenty-eight Y\`{a}ngb\v{a}n fled, using a combination of enhanced speed and flight.  The remains of the dead member were left behind.



``I can't tell if this is a good thing or a bad thing,'' I commented.



``With luck, they've changed their minds and we have much-needed allies,'' Defiant said.



``And if they haven't?''



He didn't reply.



More of Dragon's craft were arriving, adding their attacks to those of the others.  I could recognize the wheel-dragon, using some sort of tuned electromagnetic \emph{pull }to draw away the loose rubble from beneath Behemoth\emph{.  }He sank nearly ten feet as the ground shifted around him.



He struck the wheel-dragon with a bolt of lightning, flaying off a few plates of armor and destroying the wheel.  It opened its mouth and launched cannon-fire at him.  The shells exploded into blobs of containment foam, fireproof, sticky, virtually impossible to remove.



But not capable of holding back something like Behemoth.



More lightning was unleashed, each doing successively more damage to the craft.  By the fourth blast, it wasn't operational.  The fifth split it down the middle.  Insulation was little use against a dynakinetic that could redirect the natural course of electricity.



Ten craft were around him now, concentrating fire.  Cryogenic beams, containment foam and more served to slow him down.  Not \emph{stopping }him.  No, that was too much to hope for.  His pace was roughly two-thirds the speed it might otherwise be, at a glance, his attention focused on the A.I.



Behemoth brought both hands together, but it wasn't to clap.  Instead, he directed a stream of lightning at the nearest craft, easily twenty feet across.  It was splintered in an instant.



A second craft perished a second later.



Before he could turn his attention to a third, the stream of lightning shifted, curving off to one side.  Drones, the annoying little bastard spheres that had electorcuted me on multiple occasions, the same ones that had been built into the ceilings of the cells and prison hallways in the PRT headquarters, were in flight, deployed by a drone-ship like the one I'd fought in Brockton Bay, and they were channeling the lightning along a different path.



Behemoth wasn't one to roar, but I could see the effort at work as he began to draw the lightning away from the remote drones, forcing it to take another path, beyond the route of ionized air or the electromagnetic charge that they were using to catch it and harmlessly redirect it into an area that was already rubble.  He was taking abuse from the airborne craft, unable to move without giving ground.  More containment foam and more ice built around him, tearing and melting, respectively, in response to his lesser movements.



They moved closer together, strengthening the bond, and the lightning was caught once more.



He gave up on the lightning and blasted the drones out of the air with a wave of heated wind.  An instant later, he resumed destroying the craft.  Three in as many seconds, and then a slam of one claw against a building.  The shockwave that followed leveled a whole row of buildings.



I belatedly swallowed a radiation pill and attached the armband.



The screen displayed text:  `\emph{Name}?'



``Weaver,'' I said.



The letters appeared on the screen.  I confirmed with a press of the button.



A map of my surroundings appeared, a landscape rushing by.  In one corner, the distance to Behemoth was noted, rapidly counting down.



I could see the runway an instant before the ship touched down.  The rosy glow was still present as the ship cut back on forward thrust.  The craft touched the runway belly-down, skidding to a near-stop.



The red tint that surrounded everything disappeared, and Defiant caught my arm with one hand, holding on to a beam in the ceiling with the other.



The ship activated one thruster, and the craft swung around.  The other thruster kicked to life, and we took off, still bearing some of the forward momentum from earlier.  We were moving in a near-perpendicular direction to the one we'd been traveling earlier.  Defiant let go of my arm.



When I looked back at the screen, nearly half of the city was on fire.  Black smoke choked the skies, a stark contrast to the cloudy sky of only minutes ago.



``Were they able to evacuate most?'' Defiant asked.



``No,'' Dragon answered.



Our craft touched ground, and I glanced out the window to see a sliver of what the monitors showed.  A sky choked by darkness, a city aflame.



The glow of his single eye cut through the smoke, and I was reminded of \emph{Lung}.  Of that first night, on the rooftop, when one of Lung's eyes had been swollen shut, the other open.  Lung, like Behemoth, had been virtually untouchable.



This was that same scenario, that same fight.  I couldn't hope to win.  At best, I'd manage a distraction, a momentary handicap, but he'd recuperate, and given the chance, he'd murder me with a casual ease.



This wasn't a rooftop, but there wouldn't be an easy means of escape.  And just as I'd acted to stop Lung from hurting what I thought were innocent kids, I was acting here to save lives.



The same thing, but on a far greater scale.  The danger, the stakes, all scaled up by a thousand times, a million times.



The back of the craft opened, and Defiant led the way as we made our exit.  Spotlights cast much-needed light on the immediate surroundings.  The ships had settled in a ring formation, some posed above the others, as if providing a protective enclosure.  Weapons were directed outside, and one craft loomed overhead.  For now, we were as safe as we could hope to be.



Chevalier, Rime and the rest of his new Protectorate were all in one group, backed by their respective teams.



A nearby crash made half of the people present, myself included, nearly jump out of their skin.  It was somehow reassuring that Chevalier managed to retain his composure.



``The ships have all arrived,'' Chevalier said, ``I've received the data on the other participating teams, those not already fighting will reinforce as they're able.  We should expect record numbers, we \emph{shouldn't }expect it'll help.  Any news on the locals?''



``Gathering and setting up defenses at India Gate,'' Rime said.  ``It seems to be his destination.''



``The gate?  There's nothing there,'' Chevalier said.  ``Only population.''



``If it's not a soft target,'' Revel said, ``then we can play the long game, buy time for Scion to arrive.''



``Let's assume it's soft.  We made that mistake once, never again,'' Chevalier said.  ``Okay.  Listen up!''



He raised his voice, commanding the attention of everyone present.



``We've already notified you if we believe you have the capacity to \emph{engage} Behemoth.  Anyone else is operating as search, rescue, and support.  Maintain\emph{ }a distance of at \emph{least} a hundred feet from Behemoth at the very minimum.  Get any closer, you probably won't have a chance of escaping if he decides to close the gap.  Be mindful of line of sight, because he can and will tag you with a lightning bolt, and it's not something you can dodge.  Assume every structure will fall down in a heartbeat, and know that there's no good place to hide and wait for this to be over.  Keep moving and \emph{move smart}.''



The crowd of heroes was utterly silent.  I could see the Undersiders on the opposite end of the enclosure.  The spotlights behind them rendered them little more than silhouettes with glowing edges.



``There's no sugarcoating it,'' Chevalier said.  ``The fact that you're here, today, knowing the state things are in, you're the biggest damn heroes I've worked with.  I'm not going to make any big speeches.  Better we get out there and save lives.  Hit him hard if you see the chance, keep an eye out for whatever his goal might be, communicate with other groups as best as you're able.  Stay spread out so he can't wipe too many of us out at once.  You work best with the people you know, so form your own teams, stick with the people you've operated with before.  \emph{Go}.''



Heroes, already gathered in their groups, mobilized.



I started to approach the Undersiders.  Defiant's hand on my shoulder stopped me.



I could see Tattletale and Accord stepping off to one side, talking.  She gave me one glance, offered me an apologetic half-frown, and then continued walking.



``Why?'' I asked.



``The Chicago Wards,'' he said.



``What about them?  I can function better alongside the Undersiders.''



``Dragon thinks you can contribute just as much or more with the Wards group, and they're the team that \emph{wants} you.''



I glanced at the groups that hadn't departed yet.  Some were getting geared up, another group had a cape touching each member in turn, turning their skin to what looked like stone.  On the far end, past those other groups, I could see Tecton, Grace, and Wanton with three others I didn't recognize.  They were looking at me.



``It's the smart choice,'' he said, ``But it's your choice.''



And, giving evidence to the statement, he departed, entering the Pendragon and freeing me to decide without his influence.



I sighed, then activated the antigrav panels to give myself some forward thrust, speeding me up as I moved to join Tecton's group.



``Yep,'' he said, to one of the newbies.



``You're leader, I'm recon?'' I asked.  ``Like it was in New York?''



``No, you're leader as long as this fight lasts,'' Tecton said.



I must have looked surprised, because he said, ``You've been in two of these fights, right?  If we count Echidna?''



I nodded.



``I've only been in the one, and I was never the shot-caller.  That was a partnership between Raymancer and me, and he's gone.''



``My condolences,'' I said.



He nodded, but my focus was on the other members of the team, trying to account for the resources I had available.  Grace had changed her martial arts outfit for something with more coverage, a chainmail mesh like the PRT uniforms wore.  Wanton still wore free-flowing clothes, but he wouldn't stay in that form.



The other three\ldots A girl with bands of metal running down each of her arms and legs, with heavy gauntlets, boots and a breastplate, a mask etched to look like a feminine face, with white lenses over the eyes.  Her platinum blond hair had three individual braids, two draped over her shoulders, with the ends bound in more bands of the blue-black metal.



There was a guy in a cowl, with another metal mask, who reminded me a bit of Shadow Stalker, but he wore white, and carried no weapon I could see.



And the last one\ldots heavyset, with armor that seemed too generic.



``You're a rookie?''



``All three of those guys are rookies,'' Tecton said.  ``They cannibalized our non-core team members to supplement other groups, and--''



``It doesn't matter,'' I said.  ``I guess you three are getting thrown in the deep end.  Names?''



``Cuff,'' said the girl in blue-black armor.



``Annex,'' the cowled one told me.



``Golem,'' the last one said, his voice muffled by his helmet.



I frowned behind my mask, perplexed.  ``You named yourself after the little bastard from The Lord--''



``No,'' he said.  I could hear him sigh from behind his helmet.  ``I'm thinking of changing it.''



\emph{If not from the trilogy, then\ldots  }I fixed the pronunciation, compensating for how his muffled voice had modified it.  Right.  \emph{Golem}, from the myth.



``I get it, nevermind.  Listen, we're going to move out, and you're going to explain your powers en route.  You know who I am?''



There were nods all around.



``You're still okay with following my orders?''



Again, nods.



I saw the Undersiders moving out, along with the Ambassadors.



``We're supplementing and supporting the Undersiders for the time being.  You okay with that?''



A touch more hesitant, they nodded.



``Then let's go,'' I said.





