





Lightning ripped across the landscape, following its own path, independent, breaking every rule that electricity was supposed to follow.  It danced over the outside surfaces of houses, running across concrete and leaving glassy scorch marks in its wake.  It touched objects that should have grounded it, channeling it into the earth, but leaped for another target instead.



The Y\`{a}ngb\v{a}n raised their hands, already reacting.



\emph{Twenty-third path, fifth benefit.  Reflexes.}



\emph{Thirteenth path, third form}.  \emph{Forcefield constructions, barrier.}



The forcefields absorbed the worst of the energy.



Cody was already moving to use the thirty-sixth path to rescue anyone who'd absorbed the remnants of the shock.  None.  It hadn't touched them.  He was among the last of them to dismiss his forcefield.  The forcefields drained their reserves of energy, and weren't to stay up for too long.  They'd been drilled on this.



``\emph{Qi\textoverline{a}n ch\textoverline{u}}.''  Three ordered.



They mobilized.



\emph{Fourth path}.  Shallow flight.



\emph{Ninth path}.  Short range electromagnetism.  They skated off of the little exposed metal that was available around them, car hoods and pipes, gaining speed to augment their flight.



There were forty-two paths in all.  Forty-two powers.  \emph{No}, he corrected himself, there were forty-one now that Seventeen was dead.  More would die by the day's end.



The hope, the \emph{plan}, was to demonstrate the Y\`{a}ngb\v{a}n's strength, to show that they had the \emph{answer}, a way to defeat the Endbringers.  It wouldn't happen today, but a solid demonstration would serve to bring others on board.



They hadn't been asked.  The expectation was that they would give their lives for this.  He would have refused.  He'd dealt with an Endbringer before, and he still hadn't recovered from that chance meeting.  He'd lost everything, been stripped of friends and family both.



``\emph{Y\`{a}ngb\v{a}n qi\'{a}ng}!''  Five called out.



``\emph{Y\`{a}ngb\v{a}n qi\'{a}ng}!''  The group responded in chorus.  Cody's voice joined theirs, quieter.  His pronunciation wasn't good.  In all this time with the group, he hadn't even managed to grasp the fundamentals of the language.  Mispronunciation was punished, not by any reprimand, but in a subtle way.  They would speak to him even less than they were now, he would get less food.  Maybe for a few hours, maybe for a few days.  The thought bothered him, and the degree to which it unsettled him was more disturbing still.



Something so minor as that shouldn't have mattered so much to him, but it was all he had, now.



There was a crash of lightning, and a building collapsed, directly in their path.  Flames and smoke barred their path.



``\emph{Sh\`{e}nt\`{o}u}!''  Three ordered, his voice nearly drowned out in the noise of the building settling.  They were still moving forward, not even slowing.



The forward group hit the barrier with localized vacuums.  Individually, they were weak, but with twelve all together, flames were quenched, smaller objects levitated into the air.



Cody joined the middle group in shearing through the remaining wreckage.  \emph{Thirty-first path.  }The cutting lasers.  The first group was slowing a fraction, and Cody slowed his flight to hold formation.



The twelve members of the Y\`{a}ngb\v{a}n only accelerated, flying around the group members they had been following.  They turned solid, space distorting around them as they rendered themselves invincible and incapable of any action but their pre-existing momentum, effectively human bullets.  They tore through the wreckage, clearing a path for the rest.



He felt a rush, just being part of the unit.  Being a part of a maneuver that let them cut through a burning ruin of a building with the ease they had.



Some of that rush, he knew, was \emph{the second path}.  Magnification of powers.  Two wasn't present, she was too valuable to risk losing, but they still shared her power between them.  Each of them had a sliver of her ability to enhance the powers of those nearby.  It was the reason their powers worked to the degree that they did, a feedback loop in power augmentation across their whole unit.



There were more things feeding into his consciousness, other senses he wasn't actively tapping into.  The twenty-third path, it enhanced his perception, particularly his awareness of others, the threat an individual person posed, and enhanced his reflexes, particularly when dealing with people who wanted to hurt him.  It was of minimal use against Behemoth, but it made him cognizant of the other members of the Y\`{a}ngb\v{a}n, aware of their breathing, the noises they made as they ran.



In this way, the group subsumed him, rendered him a part of something overwhelming.  For now, in the midst of this, the deep loneliness and isolation was gone.  Language was almost unnecessary, beyond the one- or two-word commands he needed to know for particular maneuvers and directives.



Zig-zagging down the streets, they naturally settled back into their established rank and file.  With every member of the group having access to the same pool of powers, placement in the formation was a question of experience and how expendable they were.  Cody was an essential defensive asset, no use if he was taken out of action, so he rested in the middle of the group, surrounded by people who could protect him in a pinch.



Rumbles marked the collapses of taller buildings as Behemoth advanced, somewhere a quarter-mile behind them.



The heat was oppressive.  Even as they got further away from the monster, the fire only seemed to get worse.  The smoke was the worst part of it, preventing them from seeing or tracking their enemy.  It meant they couldn't see more than a hundred or so feet around them, and they didn't have any idea whether they were going to walk straight into the monster's path or wind up encircled by burning buildings.  Their flight depended on proximity to a solid surface.  It involved hovering five to ten feet off the ground while moving at fifty or sixty miles an hour.  They had another means of flight, but less controlled, one that risked putting them above the skyline, obvious targets for a lightning strike.



Was the Behemoth smarter than he looked?  Was the destruction seeded in a way that would spread?  Fires started where buildings were closely packed?



Cody could feel his skin prickling.  His mask was filtering out the smoke, but the heat, it was getting unbearable.



``\emph{Zh\`{a}n w\v{a}n},'' Ten said.



``\emph{Zh\`{a}n w\v{a}n},'' the group echoed her, their voices strong.  It was an encouragement, an affirmation.  Cody didn't know what it meant.  He'd been with them for an indeterminate length of time, what felt like years, but he didn't feel any closer to grasping the language than he had been on the first day.  He'd had help, briefly, but that had been stopped.



Every member of the group was permitted to speak freely, but virtually every utterance was vetted by the group as a whole.  If, like Ten, someone were to speak, and others were in agreement, deeming the phrase acceptable, then the response was clear.  If the statement was poorly timed, or out of tune with the group's line of thinking, then it was ignored, followed only by a crushing silence.



Cody had never experienced the adrenaline rush that Ten was no doubt experiencing over the simple act of getting a response from the squadron.  The group had never deemed his statements acceptable, because his pronunciation was poor.  He was a member of a tight-knit crowd, yet utterly, completely alone.



``\emph{T\'{i}ng}!'' one of the members in the rear called out.



They dropped to the ground, their landings practiced, wheeling around a hundred and eighty degrees by planting one foot on the ground and sweeping the other out.



His forcefield was up before he even knew what the threat was.  Individually weak, strong in formation: a makeshift bubble of overlapping forcefields twenty feet over their heads.



The glowing projectile swiftly grew in his perspective, giving him only a second to brace himself before it crashed down on the wall of forcefields.



The wave of heat was intense, even on the other side of the barrier.  It seemed almost liquid as it spilled out over the edges.  In seconds, they were surrounded in flame.  The forcefields sealed it off, prevented superheated air from burning them alive, but the viscosity meant it was resting against the forcefield.



\emph{Magma}?



They'd drilled on abstracts, on possible situations.  Attacks from any direction.  Attacks in various forms.  He'd never really considered the ideas behind dealing with magma, but he had the tools.  Being a member of the Y\`{a}ngb\v{a}n meant being constantly drilled.  They took your power, all but a fraction of it, but every member of the group had that same fraction.  Every member was expected to know how to use every power, to know when and to do it in unison with the rest of the squad.



A small handful of individuals in the C.U.I. \emph{hadn't} been brought onto the group.  Null, the cape who made the Y\`{a}ngb\v{a}n possible, was independent.  He \emph{couldn't} be a part of the whole.  Others included T\textoverline{o}ng L\'{i}ng T\v{a}, who had a power that was too slow to use, not worth the fractional decrease in power that came with including her in the network, Sh\'{e}n y\`{u}, the strategist, and Ji\v{a}, the tinker that supplied the C.U.I. with its devices, including the simulations for the drills.



It was those drills and simulations that allowed him to react a precious fraction of a second faster as he responded.  It kept him in sync with the others in the group as he joined half of them in letting his forcefield dissipate, simultaneously reaching out to apply another power.



\emph{Thirty-second path.  }Nullification waves.



The effect was short ranged, and he could see the shifting in the air as it extended, passed through the gaps in the forcefield where the magma and heated air were only just beginning to leak through miniscule gaps.



The waves generated by thirty-two served to \emph{stabilize}.  It stalled things in motion, warmed up cold things, cooled warm things.  It silenced, \emph{stilled}.



The magma cooled with surprising rapidity, but then, the power was affecting the inside at the same time it affected the outside, rather than trying to cool the outside to a degree that would extend inward.



Path thirty-two.  It made him think of Thirty-two, the \emph{member}.  The source of that particular power.  He snuck a glance at her.



She was one of four outsiders, four people not native to China.  She'd been his closest ally.  Something more.



``\emph{D\v{a}p\`{o}},'' Seven ordered.



Like the others, the maneuver was a practiced one.  The last forcefields dropped, and the group mobilized.  Odd-numbered members of the squad crouched, legs flexing, while even-numbered members, Cody included, reached out.



\emph{Path fourteen.  Vacuum spheres}.



The odd-numbered members of the group pierced the barrier of cooled magma, and the vacuum spheres scattered the shards.



Another sphere was already in the air, aimed close to them, if not at the exact same spot.



Without even thinking about it, he trained a laser on it.  Others were doing the same, or following suit.  The glob of magma, still mid-air, was separated into loose pieces, no longer as aerodynamic as it had been.  It expanded, fell short, disappeared into the cityscape between them and Behemoth.



Each action Cody performed as a part of the unit was validating, affirming.  It was a series of small payoffs for the drills he'd gone through for over a year, with smaller groups and the Y\`{a}ngb\v{a}n as a whole.  The drills had been intense, with one new situation every one or two minutes, like flash cards, only they were holograms, color coded polygons and shapes with just enough mass that they could be felt.  If they failed the scenario, the offending members of the squad would be named out loud, the scenario shuffled back into the list of possibilities, so it might repeat in five minutes, or two hours.



Cody was well aware of what they were really doing, between the six hours of drills and the twelve hours of schooling that combined lectures on the C.U.I. with traditional education.  He knew why they only got forty-five minutes in total to eat for their two daily meals, only five hours of rest a night, why every minute of the day was scheduled.



He'd always told himself that he wouldn't be a victim, that when the time came and he was indoctrinated into a cult, he'd recognize the targeted isolation, the practice of tiring him out so he'd be more amenable to suggestion, more likely to conform.  He'd told himself that he would rebel and maintain his individuality.



So stupid, to pretend he had that degree of willpower, in the face of crushing social pressure and exhaustion.  It had taken him nearly five days after he left the basic training and joined the official team before he realized what was going on.  The saddest part of it was that he was fully aware they were brainwashing him, indoctrinating him, and there was nothing he could do about it.  Despite himself, despite the pride he'd once had as a person, he \emph{wanted} acceptance.



They were a poor surrogate, a surrogate he hated, in a way, but he had nothing else.  His family was a universe away, his friends had turned on him, gone mad.



There was a crash, and a shockwave ripped through the area, momentarily clearing the smoke.  Cody instinctively raised his forcefield.



Behemoth was there, standing amid leveled buildings, fighting some flying capes who strafed around him.  He had built up some steam, and lightning coursed over his gray flesh, illuminating him.  Only one or two of the metal ships were still fighting.  Other craft, airborne, seemed focused on evacuating, but it was a gamble at best, as shockwaves and lightning struck them down.



The smoke filled the sky once more, obscuring Cody's vision too much for him to see any further.



Behemoth clapped again, then again, each collision of claw against claw serving to extend the damage one step further, clearing obstructions out of the way for the next.



The Y\`{a}ngb\v{a}n backed away, spreading out inadvertently.  Cody could feel the benefit of the second path fading, the enhanced powers the others granted slipping from his grasp.



``T\textoverline{a} sh\`{i} f\'{u}sh\`{e} ku\`{o}s\`{a}n,'' Three said.  He said something else that Cody couldn't make out.  Something about leaving.



The group moved out, flying low to the ground, and Cody was a fraction of a second behind, pushed himself to make sure he was in formation.



``Radiation,'' Thirty-two said, her English perfect, unaccented.  It was for Cody's benefit, and the benefit of the other two English-speaking members of the group, who might not understand the more complicated words.  She got glances from the other members of their squad, but continued speaking.  ``He's using the shockwaves to spread irradiated material across the city.  We're retreating, okay?''



Cody nodded, but couldn't bring himself to speak as the group took flight.  It was unnecessary, wasn't worth it when he accounted for how the others would react and respond if he used English.  Thirty-two would be shunned for doing so, there was no need for him to join her.



An explosion of smoke bloomed out in front of them.



Not smoke.  Darkness.



The Y\`{a}ngb\v{a}n collectively dropped into fighting stances, ready to use any power the instant it was called for.



Villains stepped out of the smoke, and it was only then that the benefits of the twenty-third path belatedly granted the Y\`{a}ngb\v{a}n their ability to sense \emph{these} people.  The power had been blocked by someone or something in the group.



They were Westerners, by the looks of them.  Cody's eyes narrowed as he studied them.  A guy with a demon mask, surrounded by the same eerie darkness that formed a wall between the group and Behemoth, a young girl with a horned mask, a stocky guy or girl with a thick fur ruff on their hood, and a girl in black with an opaque pane over her face and a crossbow in her hands.



The other group was also mounted, but clearly distinct in style, even if they'd shuffled together with the other group.  The boy in medieval clothes with a silver crown, the girl in a frock, two grown women in evening gowns.



They were all mounted on mutants.  He had to reach for the name.  The guy from Boston, Blasty?  Blasto.  He was supposed to make horrific mutants.  Maybe he was here.



The Y\`{a}ngb\v{a}n edged around the group, wary.



``Jesus,'' the man with darkness shrouding him said.  His power was billowing out around him, more darkness.  ``What the hell are you doing?''



\emph{He's getting the benefit of the power boost, }Cody thought, but he didn't speak.



The others were shifting uncomfortably, but the one with the white mask and silver crown, and the two in the evening gowns\ldots they seemed to take it more in stride.



Something about them, it tugged at a memory.  Not a strong memory, but a brief encounter at some point\ldots it gave him an ugly, twisting feeling in his gut.



He blinked, and the girl with the gray, horned mask was right in front of him. He resisted the urge to react.  His teammates, he knew, were raising their hands in anticipation of a fight.  They were distrustful.  They'd been taught that foreign heroes were dangerous, unpredictable.



Thing was, they were \emph{right}.  As a rule, capes were fucked up.  \emph{People} were fucked up.  The Y\`{a}ngb\v{a}n, Cody mused, resolved the situation by stripping capes of their humanity.



She turned around, as if she hadn't just appeared in front of him.  ``Shit, you weren't kidding.  It gets stronger as you get closer to more of them.  I can do practically anything, and they don't react.''



``No idea,'' the man in black said.



``They're Chinese capes,'' a woman in a yellow evening gown said.  ``They probably don't speak enough English to answer.''



Something nagged at him.  Cody searched his memories.  Between the crossbow and the boy in the renaissance era clothes, he couldn't help but think of the game he'd played with his friends before everything went horribly wrong.  But the evening gowns, those masks\ldots



\emph{Accord}.  The bastard who had taken him, who had traded him to the Y\`{a}ngb\v{a}n for money.



The anger was refreshing, startling, and unexpected.  A splash of scalding water to the face, as if waking him from a dream.



``Thirty-six!''  It was Thirty-two calling.



``Thirty-six?'' the girl with the horns asked.  ``What?''



It was Cody's name.  His new name, rather, but he'd never quite identified by it.  He turned and realized he'd dropped out of formation.



``Let's go,'' she said.



He glanced back at the woman in yellow.



``I can guess what you're thinking, but it's not worth it,'' she said.



\emph{Every step of the way, I got fucked.  Fucked by Krouse, fucked by the Simurgh, fucked by Noelle, fucked by Accord}, \emph{fucked by the fucking Y\`{a}ngb\v{a}n.}



The woman in yellow spoke.  ``Whether it's answers, or revenge, or something else entirely, you won't find any of it here.''



Others in her group were looking at her in surprise, or as much as one could, when wearing masks.



``Do you know how easy it would be to kill you?'' Cody asked.



Three gave an order in Chinese.  Incomprehensible, but Cody could guess.



``If you killed me,'' the woman in yellow said, ``He'd barely care, and you'd spend the rest of your life in a hole that Ziggurat made, if they didn't just paralyze you from the neck down and leave you alive to borrow your power.''



\emph{Ziggurat?  Oh.  T\textoverline{o}ng L\'{i}ng T\v{a}}, \emph{the earth mover}.



She'd said she didn't have answers, but this-



The ground shook violently.  Behemoth was still active.  Lightning was arcing through and around the dark clouds of smoke that were rising at the edges of the city.



``If it's alright, we should go,'' the darkness man said.  ``Things get much worse, I'm not sure how much we can help, and I'm losing my mind waiting like this.''



There was a whistle from someone in the group, and they were gone, the mutant quadrupeds breaking into a run.



And Cody was left standing there, staring.



Three snapped something, and Thirty-two translated, ``He's saying we can send you back, if--''



``No.  It's fine,'' Cody said.  He turned and fell into formation.  The disapproval was like a weight on him from all sides.  He withered a little.  How many weeks, months or years would it be before he was allowed to hold a conversation with his comrades?



More heroes were running by, now.  A group of young heroes, a cluster of religious capes with halos and crosses worked into their costumes, and a fresh wave of mechanical ships.  The reinforcements had arrived.



Eight said something, but the accent was too thick for Cody to make it out.



He'd been stirred from a delirium, a state where the days had blended into one another, where the sole defining moment of his \emph{week} might be if he were acknowledged by the other members or rebuked.  It wasn't Behemoth who'd shaken him from that point.  It was the woman in yellow.



Anger twisted in his gut, and it wasn't going away.  He found himself holding onto it, embracing it.



As if it reflected the violence within Cody, the city was burning, shattered and gripped in chaos.  Thousands were in the streets, running between flimsy looking buildings crusted with signage, or lying dead, struck down by shockwaves created by a monster half a mile away.  Women, children.



They passed injured, and didn't spare a second glance.  A family of five were caught in a ring of burning structures, and the Y\`{a}ngb\v{a}n didn't even spare a second glance.



\emph{We're military, not heroes}.



The goal was to fight the monster, to support the Y\`{a}ngb\v{a}n and support the C.U.I. in any way possible.



Three changed course, and the rest flew after him, setting down.  Their destination was a flattened building, with a group of dead, maimed and dying Indian capes lying in the debris.



Cody exercised the twenty-third path to find out what Three surely knew already.  There was nobody nearby.



Three reached down, and others around him joined in, making contact with one of the dying.



It took nearly a minute, to attune everything the right way.  But the effect took hold, and the injured hero disappeared.



Five looked to Cody and pointed at the next one.



\emph{Lowest rung on the totem pole.  If I didn't think Null would rescind my powers, I'd kill you here and now.}



Reluctantly, still stewing with anger, he obeyed, kneeling by the body.



\emph{The forty-second path.  }Teleportation. \emph{ }He could see the destination in his mind's eye, like an annoying spot of light in the center of his vision, gradually getting more detailed and focused.  Each person that joined his side to assist sped the process along.



The wounded hero flickered and disappeared.



By the time they were done, all three bodies had been removed.



``\emph{Qi\textoverline{a}n ch\textoverline{u}}.''  Three ordered.



They moved out.



As they traveled, he could see the streets choked with evacuees, a virtual tide of people, rickshaws, bicycles and cars.  They'd reached bottlenecks, points where they couldn't advance, and the evacuation wasn't proceeding.



Was this an extension of Behemoth's strategy?  The major streets were unused, either because the Endbringer could see them, unleashing waves of electricity and shockwaves to strike down anyone who tried those routes, or because buildings had been felled and they were impassable.



The heroes who weren't helping with the evacuation were establishing perimeters, staggered lines of defense.  Here, Indian capes were setting up turrets on high ground, guns the size of cars, drilling them into the roads and rooftops.  Another block over, there were civilians who weren't running.  They'd gathered, and were talking in low voices.  They radiated a different degree of power, on par with the capes on the rooftops.



The Y\`{a}ngb\v{a}n squadron slowed down as the cluster of capes grew denser, the buildings more solid and further apart.  There were trees here, but the heroes were cutting them down.  Each squad seemed to be executing a different plan, a different setup.  What appeared to be force-field fences were being erected in between each group and Behemoth's estimated point of approach.



There was one group with heavy ranged weapons.  An area was being cleared, set up with devices.  Another area had been marked off with chalk, but it wasn't clear what they intended to do.  Tinkers everywhere were setting up.  A kid with red armor and lenses had two odd-looking cannons set up on one rooftop, each the size of a city bus.



It painted a picture, formed a script of sorts, for the story that had yet to take place.  The idea that Behemoth would change direction from where he'd initially started off wasn't even a consideration.  They weren't consolidating forces, gathering together for one good strike, but were arranging it so one would follow after the other.  The capes he'd already seen were the ones that had gone forward to support, to find the injured, trusting to mobility or evasion to slip away.



And here, this far in, a dozen countermeasures were being set up, if not two dozen.  This would be the staging ground, without the crush of flammable buildings all around them.  Each countermeasure would occupy Behemoth for just long enough that the heroes could manage a barrage of attacks.



The Y\`{a}ngb\v{a}n reached the center of the network, landing on the rooftop with the most capes.  The makeshift command center.



He only had to take one look, and he knew.  Something vital was missing.  They had any number of ways to stall, and each one would cost them a little.  But for all of that, he couldn't make out anything that looked like it would end the fight.



Cody could see the heroes react as the Y\`{a}ngb\v{a}n landed, and he could see the way others looked to one small set of people for cues.  The top-level guys, the leadership of the Protectorate.



A a man in gleaming armor extended a hand to Three, who'd stepped away from the group.  ``We didn't expect the Y\`{a}ngb\v{a}n.''



Three looked over his shoulder, and Thirty-two stepped forward.  Three murmured something, and she translated.  ``Your PRT was very persuasive, Chevalier.''



``I suppose we can count that as a good thing.  You read the briefings and plans we sent out?''



Thirty-two continued to translate, ``We did.  With your permission, we'll return to the fight with Behemoth shortly.  But we'd like to make a proposal.''



``I know what you're going to propose,'' Chevalier said.  ``I'm sorry, it--''



``It's somewhat counter to our usual offer,'' Thirty-two spoke quickly to match Three's attempted interruption.



Chevalier fell silent.



``Your heroes here are scared.  They want to help, they are good people.  We're offering another way.  They can help without risking their lives.''



``I think I understand.  You have to understand why I'm saying no,'' Chevalier said.



``Our group shares powers.  Time and time again, the West has refused them.  We would rehabilitate your criminals, and share their powers among us.  They are divided in strength, but we have the ability to magnify powers.  You can feel it now, being close.''



``Yes,'' Chevalier said.



In the distance, a column of lightning cut through the wall of smoke above the city, as big around as an apartment building.  Cody could feel the vibrations shudder through the building, as sturdy as it was, though the lightning was miles away.



``We might each have only a share of a power, reduced effect, range or duration, but we regain as much as a third of that power back with this magnification, depending on how many are together.  A full third of forty powers at once.  If any would volunteer, we would teleport them to a safe place, where we would borrow their power for this fight only.  We would send them home when the fight was over.''



Cody could see the reactions of the capes on the rooftop.  People were exchanging glances.  Considering it.



A part of him wanted to scream, to warn them, whatever the cost to him might be.



``I see,'' Chevalier said.



``For years, we have boasted of the strength the Y\`{a}ngb\v{a}n offers the world.  But we are small, and too many citizens with powers flee or fight rather than cooperate.  Today, we hope to show our strength.  We have extended our support, and we ask for trust in exchange.''



``Your support is welcome, and that's why we couldn't ever ask you to make this leap of faith,'' Chevalier said.  ``I understand your motives are pure, but if some accident transpired, and a good cape \emph{didn't make it back}, it would mean war.''



Cody hadn't missed the way the hero had stressed the words.  A warning for his people, more than a statement for Three.



``We would be exceedingly careful,'' Thirty-two translated for Three.  ``Rest assured.''



Cody was watching the negotiations continue, Chevalier looking more and more uncomfortable, when he saw \emph{him}.



Accord.  He was accompanied by a girl in a lavender and black costume, and a dark-skinned man in a suit.



Cody had to hold himself back to keep from striking the man.  It would be suicide, and no matter which power he used, Cody couldn't be sure he could guarantee a kill.



He could see the moment where Accord saw the Y\`{a}ngb\v{a}n.  Cody could see the reaction, as if the man had been slapped in the face.  Accord's shifting mask gave away his reaction, and then his expression set, his body language neutral, as if nothing had happened and nothing was wrong.



The girl beside him smiled, and brilliant green eyes settled on Cody, stark contrasts to her pale purple costume.



He hated not knowing anything, being cut off by language barriers and the rules of the Y\`{a}ngb\v{a}n.  Who was the girl in lavender?  Where were Alexandria, Eidolon and Legend?



Every question left him more uneasy, increasingly angry, and Accord was the person who had put him in this situation.



\emph{I'm a slave, and he's the one who put me in chains.}



``May I interrupt?'' Accord asked.



``If the Y\`{a}ngb\v{a}n will excuse me?'' Chevalier asked Three.



Three nodded.  ``As you will.  We can wait.''



Cody suspected Chevalier had been hoping to end the conversation, rather than postpone it.  He stared at Accord.  \emph{Do they know what you do?  What you are?  }



There was a crash, a clap of thunder, and a rush of hot wind.  The cloud of smoke around Behemoth's battlefield was growing, and it wasn't just a matter of perspective, of Behemoth getting closer.



Capes flew off, joining the fray.  The Y\`{a}ngb\v{a}n remained.



``What can you tell us?  Do you have a plan?'' Chevalier asked Accord.



\emph{I'll kill him.  I'll kill him.  Somehow.  I just need a chance.}



It was too much, like being asleep for months and finally waking up, only to discover that the only thing inside him was rage.



``\ldots{}optimal timing,'' Accord was saying.  ``I'm still working out the particulars.''



\emph{Krouse thought he was smart too.  When I'm done with you, I'll find him and kill him.  }



``What do you need?''



``Contact information for your various squads.''



Cody virtually twitched with a need to move, a craving to fulfill some deep-seated desire for revenge, but the group around him wouldn't afford him the chance.  Each member of the Y\`{a}ngb\v{a}n was simultaneously a prisoner and a guard, some more of one than the other.



Chevalier nodded.  ``You'll have it.  Rime?''



A woman in blue limped forward, ``I'll handle it.''



The girl in lavender glanced at Cody before falling in step with Rime and Accord.



Had she sensed his emotion?  She hadn't said a thing.



``He just reached the first perimeter,'' someone reported.  ``Tore through our skirmishers.  Some teenagers were killed.  Eidolon and Legend are fighting, but they're not in good shape.  We didn't expect him to move this fast.''



``The Triumvirate's missing a key member,'' Chevalier said.  ``Our more mobile capes should move out \emph{now}.  Meet him at the first perimeter if you're fast enough, hold at the second if you aren't.  Maintain cover where possible.''



``\emph{Qi\textoverline{a}n ch\textoverline{u}}.''  Three ordered.



The negotiations were over, it seemed.



But he could feel the tickle of new powers taking hold.  The three they'd collected from the shattered building were joining them, like it or not.



The first power was an easy one to grasp.  He could feel his body surging with some added strength, and that strength swelled a step further as the power-enhancing auras took hold.



The second was a tinker power, he was almost positive, or it was a thinker power with a focus on guns.  Nothing useful.



The third\ldots another thinker power.  His vision clarified a step.  The ability to see through smoke?



No.  The ability to see through surfaces.



He was disappointed, and he couldn't be sure why.  What had he wanted?  What did he want, in general?



Even now, he was alone.  The Y\`{a}ngb\v{a}n wanted to collect capes, to prove themselves.  The heroes wanted to stop Behemoth.



Cody didn't care about either.



He entertained the notion that helping Behemoth go loose would almost be \emph{better}.  It could mean the end of the Y\`{a}ngb\v{a}n, Accord's death.  Even Trickster's death, if they had decided to show up.



Except there was no reasonable way he could do that.  Not for a lack of \emph{wanting to}, but because he couldn't hope to oppose the Y\`{a}ngb\v{a}n and the heroes at the same time.



Needed an opportunity.



The Y\`{a}ngb\v{a}n passed through the worst of the smoke, into the blasted, shattered ruins of the city.  In the moment they joined the fight, Cody held back.



They sensed he was gone, but they couldn't disengage, not as Behemoth gathered up a ruined section of building and melted it down, hurled massive globs of melted plastic, metal and stone at them.



The process took a minute at the best of times, with help.  His destination couldn't be a distant one, and he couldn't hope to behead the Y\`{a}ngb\v{a}n on his own, not with the members they'd kept in reserve, the precious ones, with powers they couldn't afford to lose, like Two's.



He nearly lost his concentration as a massive crash knocked him off his feet.



\emph{The fight's only beginning}, Cody thought.



The teleportation took hold, and he found himself back at the building the Y\`{a}ngb\v{a}n had just left, three stories down.



The command center.



Accord, the lavender girl, and Chevalier were leaning over a table with computers arranged along it, papers strewn out across the surface.



It brought back memories of the moment everything had turned upside down, the computers, the interrupted tournament.  Finding themselves in another world\ldots



If he needed a push to act, that was it.  The biggest one first.



The laser didn't cut the armor.  It was capable of cutting granite like a hot knife through butter, but it didn't cut the armor.  Chevalier turned, drawing his sword, a six-foot long beast of a weapon.  The armor glowed orange as the laser concentrated on his belly.



``You lunatic!'' he shouted, charging.



Cody switched tactics.  A forcefield-



The sword shattered it with one swing.



He flew out of the way as another swing came within an inch of decapitating him.



A laser with one hand, a vacuum sphere with another, pulling Chevalier off balance.



Again, it didn't work.  The man barely reacted as the vacuum sphere caught his legs.  He aimed his weapon, and a combination of danger sense and a nullification wave stopped the shot in the chamber, disabling the gun.



The x-ray vision was barely penetrating the sword or armor.  Cody had to duck, back up and rely on his enhanced reflexes to avoid Chevalier's attacks.  He had forty-four powers and not one was letting him beat, what, a swordsman in a suit of armor?



It was the lack of the power boost.  The Y\`{a}ngb\v{a}n were only strong as a group, granting the aura to one another.  Here, now, he was feeble.  Forty powers, and not one of them sufficient.



\emph{Always second best.  Always alone}, Cody thought.  \emph{No.}



Keeping the laser trained on Chevalier, he used his own power.  \emph{Perdition's} power.  The thirty-sixth path.



Chevalier was moved back to where he was seconds ago.  Cody backed out of the way, kept the laser trained on the hero, and the instant his opponent got too close, he used his power again.  It barely set Chevalier back two seconds, but it was enough.



Slow, steady, inevitable progress.  Time was one of the fundamental forces of the universe, undeniable.



Accord and the girl in lavender made a sudden attempt to run to the door.  Cody created a forcefield to bar their way.



They reached for phones.  He used a vacuum sphere to pull them away.



It took nearly a minute to cut through Chevalier's armor, using the time reversals to effectively put the man on hold while he put some distance between them, and the laser to cut.  The man folded over the second the laser pierced flesh, cutting straight from the front of his stomach to his back.



\emph{Obstacle gone}.



``Reckless,'' Accord said, sounding more sad than afraid.  ``Lunacy.''



``I don't care what you think.''



``I'd hoped your placement with the Y\`{a}ngb\v{a}n would temper you.''



Cody lashed out with the laser.  Accord's right arm was lopped off.



Another cut, for the right leg.  Accord screamed as he fell.



The girl in lavender hadn't reacted, only stared down at the two dying men.  She clicked her tongue, ``Tsk.''



``He's asymmetrical in death,'' Cody mused.  ``There's a justice in that, isn't there?''



``If there's irony here, it's the fact that his desire for order led to \emph{this},'' the girl commented.  ``We just lost our strategist and our field commander, so there's going to be more chaos than ever.''



The windows briefly rattled with the shockwave of one of Behemoth's attacks, halfway across the city.



``Tsk.''  the girl said, again.



The anger still burned inside him, not sated in the slightest.  \emph{Did I end it too quickly?  Maybe I should have drawn it out more}.



He glanced at her.  She was staring at him.  ``Can you use that computer to find someone?  If they're here, or somewhere else?''



``I can,'' she said.



``Trickster.''



She raised an eyebrow.  ``Oh, I can tell you that without looking.  He bit it.  Some freaky monster calling herself Noelle freaked out, made clones of him.  They ate him alive.  Literally.''



He blinked.  ``When?''



``A month ago, Brockton Bay.''



The details fit.  Cody nodded slowly.  He wasn't sure how to feel about that.



``Sorry, if he was your friend.''



``He wasn't,'' Cody snapped.  He felt off balance.  This was so unexpected.  How was he even supposed to react to that?  How long had it been since he'd really made a call on his own?



Slowly, he spoke, as if sounding out the ideas as they came to him, ``No.  I suppose that's good.  Thank you.  I'd tell you I'll make it quick, but\ldots you worked for him.  You probably deserve it.''



``Nuh uh,'' she said.  She'd backed away, gripped the edge of a table.  Her entire body was rigid.  ``I'll give you my phone, you can call any one of my buddies, tell them it's Tattletale.  They'll tell you we were constantly fighting. Only reason we haven't offed each other is that it'd be mutually assured destruction.''



``Trickery.  No, knowing him, knowing the kind of people he associates with,'' \emph{like Trickster}, ``there's probably contingency plans.  I won't fall for that.''



``Spare me, maybe I can salvage this mess.  I mean, you've still got to live on this planet, right?  We can't let Behemoth win.  Not today.''



``I'm dead anyways.''



``Because of the Y\`{a}ngb\v{a}n.  I could help.  I'll figure out a way for you to escape.  Hopeless as this feels, there's a way out.''



``No,'' Cody shook his head.  He felt so lost, so tired, so \emph{unsatisfied}.  There was one major enemy left to eliminate, one more group who'd wronged him.  The Y\`{a}ngb\v{a}n.  He already knew he wouldn't get any more satisfaction from it.  He knew he'd likely die in the attempt.  ``No, no point.''



``Fuck,'' she said.  ``There's definitely a point.  Just\ldots give me a second, I'll think of it.  Shit.  Sucks I don't know much about you.  Don't suppose you'd give me a hint?''



He raised a hand, pointing at her.  ``No.''



``Think about \emph{her},'' the girl who'd called herself Tattletale blurted out the words.  ``What would she think?''



He hesitated.



Her?  The first person that popped into mind was Thirty-two.  The Y\`{a}ngb\v{a}n member who'd tried to teach him Chinese.  They'd been close, had been friends, before the group segregated them, because they were more malleable as individuals than as a group.  Members of the same team, but never given a chance to talk with one another.  Always in arm's reach, never together.



The second person he thought of was Noelle.  His first love, the betrayer, the monster.



He shook his head, which only intensified the ringing in his ears.  When had that started?  With the shockwaves?  During the fight with Chevalier?



Or before all that?  Before the Y\`{a}ngb\v{a}n.  Had it ever \emph{stopped}?



He thought of the Simurgh, thought of all of this in the context of him being just one of her pawns.



His head hung.



Always a pawn.  Always the expendable one.  Kicked off the team, traded away to Accord for the team's safety.



``There's\ldots'' he started to speak, then trailed off.  She didn't interrupt him.  ``Who?  Which her are you talking about?  Which \emph{her}?  Be clear.''



He approached Tattletale, gripping her throat, feeling the added strength of the newest additions to the Y\`{a}ngb\v{a}n.



Tattletale's voice was strained, ``Honestly?  I figured I'd toss it out there.  There's bound to be someone important, and saying \emph{her} gives me a fifty-fifty chance.''



``I hate smartasses,'' he said, and he squeezed, feeling her windpipe collapse in his grip.



She fell to the ground, and he watched as she struggled for air that didn't come.



The faint screaming rang through his head as he watched her struggle to climb a chair, taking ten, fifteen seconds to just get her upper body onto the seat.



She found a plastic pen, collapsed to the ground with it in her hand.  When she flopped over onto her back, it was broken.  She'd caught it between her body and the ground.



\emph{This'll have to do as a surrogate for Trickster}, Cody mused, watching.  Had Noelle felt anything like this when she'd killed and devoured innocent people?  A kind of despair, mingled with helplessness?



Anger was all he had left, the drive for revenge the sole thing keeping him moving.  Feeble and misdirected as this was, it wasn't it.



Tattletale drew a knife from her belt, used the edge to remove the nib and the ink reservoir from the plastic case of the pen.



When that was done, she stabbed herself in the base of the throat.



\emph{She's giving herself a tracheotomy}, Cody thought, watching in fascination, even as he reached out and took hold of the plastic pen case.



He watched her expression as he crushed the plastic in one hand.



And he felt nothing.  Even the paradoxical \emph{grin} that appeared on her face, in contrast to the frustrated slam of one hand against the floor, it reminded him of Trickster in an odd way.  Yet it added nothing to this.



\emph{Think about her.  What would she think?}  Tattletale's words struck him.



He thought of Thirty-two, and without even deciding to, he used his own power on the pen case, returning it to the state it had been in seconds ago.



He handed it back to Tattletale, then stood, his back to her, as he concentrated.



As goals went, it wasn't much of one.  He'd barely talked to her.  As far as kindnesses went, hers had been minor at best.  But he'd save Thirty-two.



It took two minutes to carry out the teleport.  He didn't have much time before the Y\`{a}ngb\v{a}n found a free moment to contact Null and rescind his powers.  Maybe they were calling already.  Maybe the electromagnetic radiation in the area would block the call.



He'd find a way, regardless.



He felt his power take hold and teleported.  Back to the battlefield, back to Thirty-two.



Chest heaving as she greedily sucked in air through the plastic tube she'd jammed into the hole in her throat, Tattletale feebly crawled over to Chevalier.  Her strength was depleted before she got halfway.



She stared across the room at Accord and Chevalier's bodies, straining to see if either were breathing.



She managed the only utterance she could, without the ability to bring air from her lungs to her mouth:  A click of her tongue.  ``Tsk.''





