





The school's bell tolled, oddly deep, with an echo that continued, unending.  I couldn't see it through the cloudy haze that consumed my vision, but I felt as though the lockers were straining against their hinges in keeping with the rhythm.  The same went for the floor tiles, and the hundreds of footfalls of the students milling around me.  A pounding rhythm.



I couldn't keep my footing.  I was blind, still, but that wasn't the source of the problem.  It seemed vaguely familiar, the way every impact seemed designed to hit me where it hurt, to knock me off-balance and leave me in a state where I was spending too much time reeling and staggering to push back or find safety.



Someone tall shoved past me, and his bag caught on my nose.  It tore at the skin between the nostrils, and I could feel warm blood fountaining from the wound.  I staggered, bending over with my hands to my face, and someone walked straight into me, as though they didn't know I was there.  My head hit a locker and I fell.  Someone stepped on my hand as their vague shape walked by, and I could hear something break, could \emph{feel} it break.  The pain dashed all rational thought from my mind.



I screamed, brought my hand to my chest, cradling it.  I was tougher than that, wasn't I?  I wasn't made of glass, to have bone fracture or-



``You're so pathetic, Taylor,'' Emma intoned.



\emph{No.  Not now.  Not like this.}



I could hear Madison tittering.  Sophia was silent, and her presence was all the more ominous for it.  I'd done something reprehensible to her.  I couldn't recall what it was, but I knew she was here for retaliation.



They struck me, and I fell.  Emma and Madison took turns kicking me, and every effort I made to defend myself fell short.  It wasn't just that I didn't know how to fight, or that I was blind.  It was somehow \emph{worse}, as though every effort I made were being actively punished.



I'd reach out with my good hand to grab one of them and pull them off their feet, and my elbow would get stepped on, forcing it to bend the wrong way.  I tried to push myself to a standing position, only for someone to kick me in the back, slamming my chest and face into the tile, hard.



I tried to speak and a kick caught me in the throat.



And all around me, there was the steady rhythm of footsteps and the bell's echo.



The point was clear.  I was supposed to give up.  I \emph{really} should have given up.



If I wasn't able to do something on my own, maybe a weapon?  Some tool?  My thoughts were confused and disordered, but I searched through them, as if I could remember if I'd stashed some tool or weapon on my person.



No, something else, I was supposed to have another weapon, though my instinct told me it wasn't anywhere I could reach, and that was \emph{normal}.  I searched for it-



\blacksquare



\emph{The scene was visible through a thousand times a thousand eyes, the colors strangely muted in favor of texture, the images blurring except where they moved, when they became oddly sharp.}



Tattletale managed to leap back from the metal walkway as Noelle lunged and caught on the fixture.  As Noelle fell, her claws scraping gouges into the concrete walls, the walkway was pulled free.  Tattletale had put herself in one of the rooms that extended off the walkway.  Coil's room.  There was a doorway to nowhere between herself and Noelle, surrounded by concrete walls that were two or three feet thick at their narrowest point.



\emph{Most of the construction of this place had taken place after Coil had found out about Noelle.  He'd known there was the possibility that she would go rogue.}



Tattletale stepped up to the doorway, drew her gun, and fired, gunning down a Grue that had been vomited out.  Blood spattered and he went limp.



\blacksquare



-and I couldn't find anything.  I was unarmed here.



One kick caught me in between the eyebrows, and my head exploded with pain.



That spooked me.  I had to protect my head.  If I suffered another concussion\ldots



That was the breaking point.  My brain was more important than whatever else I was trying to protect.  Anything else was fixable.  I stopped fighting back, tucking battered legs against my bruised upper body, drawing my hands around my head.



Immediately, the assault stopped being an attempt to break me and destroy my every effort to stand up for myself.  It became something more tolerable, with periodic kicks and stomps instead.  The accompanying shame and humiliation was almost nostalgic.  Horrible, but familiar.



Then Sophia stepped close, and I felt something sliding beneath my hands and arms, settling around my neck.  A noose.  She used it to lift me, choking, off the ground.



Madison opened the locker, and the rancid smell of it wafted around me.  I would have gagged if I could breathe.



Sophia shoved me inside, planting one foot between my shoulder blades as she hauled back on the rope.  My unbroken fingers scrabbled for purchase, found only trash and cotton that tore when I tried to grab it.  Bugs bit at my flesh and there was nothing I could do to stop them.



Bugs?  There was something I thought I should know, something-



\blacksquare



The bugs observed as Tattletale pulled the pin from a grenade.  She waited while it sat in her hand.  It was dangerous and reckless to `cook' a grenade like they did in the movies, but then again, this was Tattletale.  It fit with her nature, and if anyone knew how long the fuse really was, it was her.  She tossed it down to where Noelle lurked below.



\emph{The grenade detonated just before it made contact, billowing with smoke and radiating enough heat to kill the bugs that were finding their way into the underground base.  Other bugs could see the shifting radiance of the flames.}



\emph{Tattletale shouted, ``Rachel!  Now!''}



\blacksquare



-that eluded me, like the water that escaped the ever-thirsty Tantalus.



As I scrabbled for purchase, the contents of the locker shifted, falling and collapsing against me, pressing tight against my body, smelling like old blood and rancid flesh.



My heart skipped a few beats and I felt as though my blood was turning to sludge in my veins, slowing down.  My thoughts dissolved into a slush of memories, speeding through my life in choppy, fragmented, distorted images.  I felt momentarily disembodied, as though the line between myself and my surroundings, my mind and my feelings were all blended in together.



When it pulled back, I could finally breathe.  I let out a deep, shuddering breath.  I could breathe.  I could think again.



I heard the sound of blades rasping against one another, the ringing of steel building with each repetition of the sound.  I blinked, and the blind haze lifted as though I'd only had tears in my eyes.



Mannequin stood in the center of the room.  He had four arms, each ending in three-foot blades, and was sharpening each weapon against the others without pause.



Around him, the factory.  Machinery churned, pumps and pistons and levers moved, and furnaces glowed to cast long shadows, casting Mannequin in a crimson light.  The people from my territory were there too, along with Sierra, Charlotte, Lisa, Brian, Rachel, my dad, and my teachers.  Each of them fought to hide in the shadows and the corners, but there wasn't enough room.



I carefully assessed the tools I had at my disposal.  My gun, my knife, my baton.  In a more general sense, there were my bugs.  I called for them-



\blacksquare



\emph{Tattletale jerked toward the doorway, stopped as one arm stretched behind her with a clink.  She'd handcuffed herself to a length of chain, fastening that chain to a rubber-sheathed cluster of wires at the far end of the room.  Tattletale's free hand gripped her gun, pointed it at something narrow\ldots The bugs who were touching the object in question were being absorbed, dying.  It was one of Noelle's tongues, wrapped around Tattletale's waist.}



\emph{The gunshot went off, severing the tongue, and the chain went slack.  Tattletale dropped to her knees, pressing her gun hand to her shoulder.}



\emph{The three largest dogs attacked.  Bitch sent three, and the result was predictable.  Noelle absorbed them as they made contact, though each dog was nearly a third of her own size.  Her flesh stretched thin around the mass of each dog, then stretched thinner as they started to swell in size.}



\emph{Noelle's flesh crept over them faster than they grew.  The growth ceased the instant the flesh finished enveloping them, and their struggles slowed.  It took long seconds for them to stop struggling, but each dog eventually went limp.}



\emph{Tattletale and Rachel watched as two figures stepped out from behind Noelle.  Regent and a Skitter.  Me.}



\emph{Regent whipped his head up in Tattletale's direction, and she dropped her gun.  As her good hand snapped up to her throat, gripping it, it became apparent that dropping the gun had been quite intentional.  If she'd been holding it-}



\emph{The perspective of the scene shifted abruptly as the Skitter bid every bug in the area, Noelle's included, to turn toward Rachel.}



\emph{Rachel clenched her fists.}



\blacksquare



-and barely any responded.  A hundred?  If that?  The heat of the furnaces killed many of the ones who were trying to approach.  It left me with a mere thirty-nine bugs.  I might as well have been unarmed.



Mannequin extended one arm with the blade outstretched, pointing at the crowd.  His `eyes' were on me as he did so, moving the blade slowly.  Pointing at faces that were familiar, but who I couldn't name.



Pointing at my dad.



And there was nothing I could do to save him.  \emph{Not} saving him wasn't an option, either.  I drew my gun, fired.



Only one bullet in the chamber.  There was a sound as it hit Mannequin, but he barely reacted as he turned toward my father.



I drew my knife and baton, charging.



Futile.  He ignored me completely, raising one hand and then stabbing down.  I couldn't even look at what was happening.  Refused to look.



I struck Mannequin, aiming for the joints, the small of his back, his hips and knees.  Nothing worked.



Without even looking, Mannequin reached over to one side and thrust one blade at me.  His weapon penetrated my armor like it was Armsmaster's special halberd.



I screamed, but it was more rage than pain.  I howled like I might against a hurricane, a storm that was destroying everything I loved, that I was helpless to fight.  I battered him, struck him with my weapons, gave everything I had and more, to no avail.



He folded his arms around me in a bear hug, squeezed, crushed.



More of him folded around me, pulling tight against my head, my throat, arms, chest and legs.



My life flashed before my eyes, every event, every memory and recalled feeling distilled into a single point.



When the crushing sensation passed, I was left standing, disoriented, in the middle of a flooded ruin.



The momentary relief faded swiftly.



All around me, desolation.  Blasted buildings, bodies, flooded streets.  Graffiti covered the walls around me, the letter-number combination `s9' repeated in endless permutations and styles.



I flinched as an explosion took the top off a building two blocks away.  Blue flames roared on the upper floors.



I couldn't breathe.  My skin prickled, burned, just on contact with the air.  I felt nauseous, disoriented.



Radiation?  Plague?



A fleet of cockroaches scurried over one of the nearby ruins, like cattle stampeding away.



They were fleeing from \emph{something}.  Multiple somethings.



I took cover.



``\emph{Where are you}?''



The voice might have been sing-song if it weren't for the filter that reduced it to a mechanical hiss.



``Where are you?'' another voice echoed the first.  Younger, female.  A girl's giggle followed.



``Hush, Bonesaw,'' Jack's voice reached me, like a sibilant whisper in my ear.  The water that flooded the streets served as a surface for the sound to bounce off of, letting it carry throughout the area.



My costume was more tatters than actual fabric.  It wasn't like there were spiders anymore.  Only cockroaches, and fewer than I might hope.  The water that flooded the streets wasn't so kind to them.



``What game shall we play today?'' Bonesaw asked.  ``Did you make anything?  Please tell me you made something.''



``\emph{I did},'' Bakuda responded.  ``I borrowed from your work for this one.''



They were close.  Nine of them.  I couldn't run without making noise.



The cockroaches, then.  I reached for them-



\blacksquare



\emph{``Regent,'' Noelle gasped out the word.  She was far bigger than she had been before.  ``Come.''}



\emph{Regent hesitated, gave her a sidelong glance.}



\emph{``Come!'' she roared.}



\emph{He reluctantly obeyed.  She raised one massive limb, slammed it into the wall where the walkway had once been attached.  The mutant Regent clambered up her arm to the doorway.}



\emph{That would be the doorway that leads to the corridor with the cells.}



\emph{The same cells where Shatterbird was in sound proof containment.}



\emph{Tattletale had descended to the ground floor and was backing up as two Skitters and a Grue approached, with Bentley advancing to her side.  Rachel was prone, lying at the point where the wall met the floor, with Bastard on the ground and pressed up against her, as if he were using his bulk to keep the worst of the bugs from reaching her.  Her other dogs were smaller.  Big, but much smaller than they could be.}



\emph{``You take fliers, I take ground?'' one Skitter asked the other.}



\emph{``Mm-hmm,'' the other Skitter grunted her reply.}



\emph{``Have to share, be smart about this one.  Grue, hang back.  She might try pulling something,'' Skitter One ordered.  ``Harder to make a counter-plan against bugs.''}



\emph{``Me?  Pull something?'' Tattletale asked.  She was cradling one arm, and covered in vomit.  Judging by the body parts that surrounded her, Bentley had taken apart the clones that Noelle had vomited at her.}



\emph{``Yeah, you,'' Skitter One said.  ``You're the type, aren't you?  Awfully fond of keeping secrets for someone who calls themselves Tattletale.  Keeping secrets from me, even at the best of times.  Even though you knew what I'd gone through.''}



\emph{``I've been pretty open,'' Tattletale said.  She retreated a step, and Bentley advanced.  The swarm stirred around the two Skitters and the Grue.}



\emph{``You haven't mentioned your trigger event, have you?  Perfectly happy to dig through other people's sordid pasts, but you won't get into your own darkest moment.''}



\emph{``Really not that interesting,'' Tattletale said.}



\emph{Skitter One's voice was thick with restrained emotion.  ``It's still a betrayal, staying silent.  How can we have a partnership, a friendship, without equity?''}



\emph{``Maybe.  I think you're exaggerating.  Does the other Skitter have any input?  Awfully quiet.''}



\emph{Skitter Two made a growling sound that might have sent a small dog running for cover.  ``I'm the quiet type.''}



\emph{``That you are,'' Tattletale said.}



\emph{``No commentary?  No manipulations?'' Skitter One asked.  ``Nothing nasty to say, to throw us off-balance?''}



\emph{``You're already off-balance enough.  Besides, I don't think anything I had to say would get through.  How can I target your weak points when you're nothing but?''}



\emph{``That so?'' Skitter One asked.  ``Doesn't happen often, does it?  You're not as cocky, now.  Do you feel scared?''}



\emph{``Just a bit,'' Tattletale said.  She'd backed up enough that she'd reached the wall.  The mangled staircase stretched out beside her, almost entirely torn free of the wall.}



\emph{``Why don't we turn the tables, then?  Let's see how I do, trying to fuck with your head,'' Skitter One suggested.}



\emph{``I'll pass.  Bentley, attack!''}



\emph{The dog hesitated, hearing the command from an unfamiliar person, but he did obey.  Skitter Two ran towards him, surrounding herself with crawling bugs.  At the last second, she took a sharp left, sending a mass of bugs flowing to the right.}



\emph{Bentley managed to follow her, struck her with his front paws, and shattered her legs.  Skitter One's flying swarm flew over him, and began binding him with threads of silk.  It was too little, a distraction at best.}



\emph{Tattletale fired her gun, and Skitter One went down.  The bullet didn't make for an instant kill, and the bugs continued doing their work.  Tattletale thrashed as the bugs started to cluster on her, took aim again-}



\emph{And the Grue swept darkness over Skitter One.  She disintegrated, reappeared as the darkness sloshed against the far wall.}



\emph{Teleporting things via his darkness.  As divergences from the base powerset went, it was pretty extreme.}



\emph{``Heroes are on their way!'' Skitter One shouted to Noelle, one hand pressed to the flowing chest wound.}



\emph{I could sense them, observing with the same bugs that Skitter One was using.  Tattletale had left each of the doors unlocked as she'd made her way into the base, and Miss Militia was leading a squadron of Protectorate members and her Wards through the series of rooms and tunnels.}



\emph{More bugs sought Rachel out, and she kicked her legs at the gap where they were flowing in beneath the left side of Bastard's stomach.}



\emph{Shatterbird appeared in the doorway at the end of the tunnel.  She was holding the Regent-clone by the throat.  She pushed him forward and let his limp body fall.  It landed in the heaping mass of Noelle's flesh.}



\emph{Shatterbird panted, her face was beaded with sweat, and it wasn't related to the scene she was looking at, not the underground base filled with flesh and bodies.  Her hand shook as she pushed her hair out of her face.  Emotion?}



\emph{Miss Militia chose that moment to open the door.  She, like Shatterbird, stared at the scene, but she was distracted as she was forced to grab the door frame to avoid stepping out onto the ruined walkway.}



\emph{Tattletale's voice was muffled by the bugs that were crawling on her face.  To actually open her mouth, in the face of all that, I wasn't sure I could have done it.  I knew better than she did what the result might be, but\ldots yeah.}



\emph{But she did it.  Tattletale opened her mouth and shouted, ``Shut the door!''}



\emph{Miss Militia moved to obey.  Too late.}



\emph{Shatterbird screamed, using her power of her own free will for the first time since we'd captured her.}



\blacksquare



-and the cockroaches obeyed.  They formed a rough human shape, then another.  Swarm-clones, as close as I could get to making them, without a concealing costume for my real self.



And the Nine didn't fall for it.  Bakuda turned my way, and I belatedly remembered the heat-tracking goggles.  She could follow me by my body heat.



I ran, and I knew it was futile.



Night caught up to me first.  It would have been a simple matter for her to kill me right then, but she had different aims.  Her claw cut at the back of my legs, and I fell, crippled.  My fear pushed the pain into a distant second place on my priority list.



In a matter of moments, I was surrounded.  Night at one side of me, Crawler on the other.  Jack, Bonesaw, Siberian, Bakuda, Shatterbird, Burnscar and Panacea.



It was \emph{Weld} who seized my wrists.



``Run,'' I tried to warn him, but the words didn't reach him.  Fluid bubbled out of my lips, and it came out as a mumble.  The radiation?  Plague?  Had Bonesaw or Panacea done something to me without my knowledge?



He said something I couldn't make out.  It sounded like I was underwater.



Then he \emph{pulled}.



He wasn't gentle about it.  He threw me over one of his shoulders with enough force that bile rose in my throat and the sharper parts of his shoulders poked at my stomach.  I tried to move my hand to raise my mask, so I wouldn't choke if I threw up, but my arm didn't respond.



My head swam, and half of my attempts to breathe were met with only chokes and wet coughs.



Was this another delusion?  A dream?  Could I afford to treat it as though it was?



I was still blind, but my power was waking up.  I could feel the bugs in the area, and I was getting a greater picture of the surroundings as my range slowly extended.



Shatterbird was still perched in that doorway-turned window.  Noelle was beneath her, and I had only the bug-sight to view her with.  Her already grotesque form was distorted further by the three dogs she'd absorbed into herself.



Instinctively, I tried to move my bugs to get a better sense of the current situation.  They didn't budge.



Instead, I felt the pull of the other two Skitters, wresting control of my bugs from me as though they were taking a toy from a baby, ordering those bugs to hurt my teammates and allies.



Rachel and Tattletale were down, and Imp was crouched beside Tattletale.  Imp had pulled up the spider-silk hood that I'd worked into her scarf, covering the back of her head, and cinched it tight.  It wasn't perfect, but it was leaving her almost totally protected.



Almost.  Bugs had reached her scalp, and there were spiders working thread around her legs.  I wasn't sure if she was aware of the latter.



The Wards and Protectorate in the upstairs hallway- some were hurt.  The fallen and the wounded were numerous enough that the heroes had lost any momentum they'd had.  Their focus was in the hallway, now, in saving their teammates.  Maybe they'd deemed the situation unsalvageable.



I exerted a greater effort, trying to reduce the impact the swarm was having on everyone present, but there was nothing.  My doppelgangers had a complete and total override, and the pair definitely noticed my attempts.  They turned my way.



What would I be doing in their shoes?  They couldn't hurt Weld, but they could hurt \emph{me}.



Or they'd find another avenue for attack.



``Weld,'' Skitter One spoke up.  Her voice was quiet.  ``Surprised you're here.  Did Imp help you get close?''



\emph{Do I really sound like that?}  I wondered.  \emph{And Imp?}



Weld wasn't replying.



``\emph{Really} surprised you're with \emph{her},'' Skitter One said.  She had one hand pressed to a chest wound.



Weld glanced over his other shoulder at her.  The other Skitter was a distance away, with shattered legs.



``Did she tell you?'' Skitter One said, ``She set someone on fire.  Maimed a minor, slicing his forehead open.  She cut off Bakuda's toes, carved out a helpless man's eyes.  I can keep going.''



``I don't care,'' Weld said.  He wasn't moving.  Why?  He was waist deep in Noelle's belly, holding me\ldots  it dawned on me that he couldn't throw me to some point clear of Noelle without giving me to the Skitter.



``You \emph{should }care.  I could tell you about the critically injured man she left to bleed out and die.  She stood by and let people get attacked by Mannequin so she could buy herself time to think of a plan to make a counterattack.''



I opened my mouth to speak, but I couldn't draw in enough breath to manage more than a hoarse whisper, and Weld wouldn't have heard me.



``I don't care,'' Weld said.  ``I know she's done bad things.  After this is over, we'll find her, beat her and take her into custody.''



``You don't care?'' Skitter One asked.  ``She murdered your boss.  Shot Thomas Calvert in cold blood, not that long ago.''



Weld froze.  Or he went more still than usual.



``Whoopsie,'' Imp said.  She'd appeared behind Skitter One.  A slash of her knife ended Skitter One's contributions to the discussion.  ``Sorry to interrupt.''



I couldn't say whether Skitter One's feedback had done anything to change his behavior, but Weld wasn't gentle when he grabbed me and flung me overhand.  My legs tore free of Noelle, where her flesh had closed firmly around my legs, and I was sent flying.



Unable to move to protect myself or react to the landing, I sprawled where I landed, fifteen or so feet from Noelle.



Weld turned back to Noelle.  His left hand changed to become a blade, and he used it to hack and slash his way through Noelle's side.  His other hand dug and scraped for purchase as he deliberately and intentionally submerged himself.



My bugs found their way to the others.  I did what I could with my bugs to drive Shatterbird away from the doorway and put her out of reach of Noelle's tongue.  Once she'd started staggering back, I set about finding and destroying the bug clones who were attacking people and ignoring my powers.



The door where the Wards and Protectorate had been lurking opened.  Miss Militia tested her weight on the staircase, then leaped down to ground level.



She trained a gun on Imp as she noticed the girl crouching over Skitter Two, the taciturn Skitter with the broken legs.  Imp executed the girl, glanced at Miss Militia and shrugged.



I tried to speak, coughed.  I pulled my bugs away from Rachel and Tattletale.



Miss Militia stared at Noelle, her eyes adjusting to the poor lighting.



``You \emph{fed} her!?'' Miss Militia asked.



``Rachel,'' Tattletale said, ``Come on!''



There was a clapping or slapping noise, and Bastard lurched to his feet.  Rachel stood, and the other three dogs spread out around her.



``You \emph{fed} Echidna?'' Miss Militia asked, disbelieving.



\emph{Echidna?  }Right.  They'd coined a name for her, then.



``And we'll feed her more,'' Tattletale said.  ``Rachel!  All of the spare dogs!  Try not to get in Weld's way!''



The dogs began to grow, flesh splitting, bone spurs growing, and muscles swelling to greater size.



Rachel hesitated.



``Do it!'' Tattletale shouted.



Rachel gave the orders, shouting, ``All of you, hold!  Malcolm, go left!''



She slapped one dog on the shoulder, and he bolted.



``Coco, go right!  Twinkie, go right!''



The other two dogs gave chase, stampeding past me as they ran along the right side of the room.



``Hurt!''  Rachel gave the order.



The dogs attacked the closet target – Noelle.  They got stuck in her like she was tar.



But, I realized, that the converse was also true.  Noelle was absorbing them, but she was unable to move so freely as long as this much extra mass was stuck to her.  It was like the way we'd fought Weld, sticking metal to him.



The problem would be when she spat out the dogs.



I tried to move, but I felt like I had fifty pound weights strapped each of my arms and legs.  My face burned hot, and my vision swam.



It wasn't an entirely unfamiliar feeling.  I felt sick.



With that thought, it dawned on me.  Noelle absorbed living things, and that apparently extended to bacteria.  Where others had bacteria in their digestive systems to help them digest food, Noelle, \emph{Echidna}, had no need for such.  When she absorbed the ambient bacteria and molds from her surroundings, she was storing them, weaponizing them like she did with rats and insects.  They were used to debilitate her victims, render them unable to fight back while her clones got the upper hand.



It meant I was sick, and I'd have to hope that whatever the illness was, it would be short-lived.



Shatterbird was still thrashing, trying to do something with her glass and failing because she couldn't breathe or see.  Echidna couldn't move, as her legs were caught on the dogs.  The other clones had been executed by Imp, as far as I knew.



The sticking point was \emph{Weld}.  Tattletale had apparently figured out that he was immune to Echidna's absorption ability, but he wouldn't be immune to her basic shapeshifting ability.  She didn't have a lot of control over her form, or she surely would have chosen something \emph{without }that number of legs, \emph{without} the three mutant dog heads, but she \emph{did} have the ability to shift her flesh around, and Weld was limited in how fast he could cut that flesh away.



Rachel had moved to my side.  She put her arms under my shoulders and my knees and lifted me, grunting.



I twisted around to cough and gag.  I managed to move one arm to my face, but didn't have the strength in my fingers to move the fabric at my neck.



Rachel found it instead, pulling it up and halfway up my face.  I coughed up lumps of stuff that tasted the way raw meat smelled.



``Careful!'' Tattletale said.  ``Incoming!  Dogs!''



Noelle had apparently moved one of her heads around, because she managed to spray a stream of vomit our way.



There was a pause as her body heaved, my bugs could sense the movement as one of the bulkier dogs was repositioned inside her monstrous lower body, and then she puked up one of the dogs, along with a handful of humans.



It wasn't large, wasn't mutant.  Well, it was \emph{a} mutant, but it wasn't one of \emph{Rachel's} mutants.



``Bentley,'' Rachel ordered.  ``Kill.''



The bulldog lunged and seized the smaller dog in its jaws in a matter of seconds, crushed it in a heartbeat.



``Yeah,'' Rachel said, her voice low enough that only I heard it.  ``Feels wrong.''



``Why?'' Miss Militia asked.  ``Why was it small?''



``When we were hanging out with Panacea during the Slaughterhouse Nine fiasco, she put her hand on Sirius,'' Tattletale said.  ``And she said that the tissues die as they get pushed out from the center.  They're more like super zombie dogs, really, with a juicy, living center.''



``And Echidna doesn't copy dead things,'' Miss Militia said.



Tattletale nodded.  ``We got lucky.  I was worried it would only be a little smaller.''



Weld was fighting to emerge.  He had his hands on Grue and one of the dogs.  He hurled them out, and Miss Militia caught the dog.  Imp and Tattletale hurried to drag Grue away.



``Did you bring all the stuff I asked for?'' Tattletale asked.



``Yes.  It won't be enough.''



``So long as you've got \emph{some}, it'll help.  Just need to buy time,'' Tattletale said.



Echidna's bulk shifted.  I couldn't see it with my own eyes, but with the blurry vision the bugs offered, I could track how she was getting her legs under her.  I could see that there weren't any distinct bulges anymore.  She was breaking down the mutant flesh she'd stripped away from Rachel's dogs and she was making it her own.  Six dogs\ldots if my estimates about them being roughly a third her mass were right, she could be three times as big as she'd been before.



``She'll be stronger,'' Miss Militia said, putting the dog down.  ``If this doesn't work, we just gave her a power boost for nothing.''



``We're saving the people she took,'' Tattletale said, ``And we're buying time.  It's not nothing.''



Echidna heaved herself up to her feet.  She vomited forth a geyser of fluids and flying clones.  Our ranks were scattered, knocked over and pushed away from Echidna by the force and quantity of the fluids.



It was stronger than before.  Whatever the source she was drawing from was, she'd reinforced it with the mass she'd gained from eating the dogs.  No less than fifteen clones littered the floor, and there were another twelve or so dogs and rats in their mass.



Miss Militia didn't even stand before opening fire.  Twin assault rifles tore into the ranks of the clones as she emptied both clips, reforged the guns with her power, and then unloaded two more clips.  Several clones were avoiding the bullets more by sheer chance than any effort on their part.  One Grace-clone managed to shield the bullets, moving her hands to block the incoming fire.  One stray shot clipped her shoulder, but she was holding out.



Echidna spat up another wave, and I hurried to get my flying bugs out of the way.  I still couldn't move, but I held my breath.  The wave hit us on two fronts, an initial crush of fluid and bodies, and the bodies from the first wave that had been shoved up against us.  As the fluid receded, my bugs moved back down to the ground to track how many clones she'd created.  It made for a pile of bodies, with snarling dogs and clones struggling for footing as they reached for us.



Bentley and Bastard provided our side with the muscle we needed to shove the worst of the enemy numbers away, bulldozing them with snouts and shoving them aside with the sides of their large bodies.  Miss Militia followed up by sweeping the area with a flamethrower.  She stopped, waiting for the smoke to clear, and Tattletale shouted, ``Again!  Weld's still inside!''



Another wave of flame washed over the clones.  They were Regents, Tectons and Graces, as well as various dogs, and none were able to withstand the heat.  Each and every one of them burned.



But this much heat and smoke, even with this space being as large as it was, it wasn't an assault we could sustain.



Echidna opened her mouth for a third spray, then stopped.  One by one, bodies were dropping from her gut.



``No!''  Noelle screamed, from her vantage point on top of the monstrous form.



Weld forced another dog free, and Echidna moved one leg to step on it.



Grace and Tecton fell, and Weld dropped after them.  He turned the blade of one hand into a scythe, then chopped a segment of Echidna's foot free.  With one motion of the scythe, he sent Tecton, Regent and some of the dogs skidding our way, sliding them on the vomit-slick floor like a hockey player might with a puck on ice.



Echidna deliberately dropped, belly-flopping onto Weld, Grace and the dismembered foot that had stepped on the sixth dog.



Miss Militia was already drawing together a rocket launcher.  She fired a shot at the general location where Weld was.  He forced his way free of the resulting wound a moment later, the dog tucked under one arm, Grace under the other.



Echidna swiped at him, but he hurled the others forward to safety a second before it connected.  He was slammed into the wall, but he didn't even reel from the blow.  He made a dash for us.



``Retreat!'' Miss Militia gave the order.



The staircase shook precariously as we made our ascent, one group at a time.  One of the capes had frozen the staircase of the metal walkway to the wall to stabilize it.  They started getting organized to hand each of us and the dogs up to the door, but Rachel barreled past, carrying me and two dogs, with Bastard and Bentley following behind.



As we reached the doorway, dogs were handed to the able-bodied.  Others were helping the wounded.  Clockblocker had fallen, and Kid Win was being moved with a makeshift stretcher formed of one of the chain-link doors that had been in the hallway.  There was a lot of blood.



It was Shatterbird's power, I realized.  I'd barely registered the event.  Shatterbird was still in the hallway on the other side of the underground complex.  Standing away from the main fighting, perhaps, or waiting for an opportunity.  She'd found the locker where Regent kept her costume, was using her power to put it on while simultaneously fighting off the bugs that were still biting her.



Echidna reared back, apparently gearing up to vomit, and Miss Militia fired a rocket launcher straight into the monster's open mouth.



It barely seemed to slow Echidna down.  Vomit spilled around her, crawling with vermin and bugs.



The monster was moving slower, now.  The entire structure shook as she advanced on us, sections of the walkway crumpling and screeching where her bulk scraped against it.



But the door was just that – a door.  Three feet wide and six feet tall.  The tunnels the trucks had used were too small for her mass, even if one ignored the fact that they'd been strategically collapsed.



The entire area shook with the impact of her furious struggles.  She was trying to tear her way free.  The violence only ramped up as we made our escape, to the point that I was worried the building above us would come down on top of our heads as we headed outside.



The warm, fresh air was chill against the damp fabric of my costume as we escaped from beneath the building.  I could sense other heroes and trucks stationed nearby, no doubt surrounding the area.



The second we'd reached the perimeter, Tattletale collapsed to the ground, propping herself up with her back to a wall.  Grue and Regent were placed next to us.



We were covered in blood and vomit, half of us so weak we could barely move.  It didn't convey the best image.



``Vista wasn't inside Echidna,'' Weld said.  ``If she's still in the building-''



``Triumph, phone her,'' Miss Militia ordered.



``Yes'm,'' Triumph replied.



Miss Militia turned to Tattletale.  She gestured at the nearby vehicles.  ``You said you wanted containment foam.''



``I did,'' Tattletale said.



``You think she'll fight free?''



``Almost definitely,'' Tattletale said.  ``She had a Grue with her.  One with teleportation powers.  He disappeared partway through the fight, lurking somewhere out of sight.  Being \emph{pragmatic} about the situation.  So unless someone can testify to having killed the guy, we can expect her to pop up in a matter of minutes.''



``Minutes,'' Miss Militia said.



``No reply from Vista,'' Triumph reported.



``Keep trying.''



``She gets free in a few minutes, and we'll use the containment foam then?'' Assault asked.  I jumped a little at the realization it was him.



``No,'' Tattletale said.  ``We'll use it as soon as the dust settles.''



``Dust?''  Assault asked.



She withdrew her cell phone, raised her voice, ``If any of you have force fields, put them up now!''



Tattletale started punching something into the keypad.  Miss Militia grabbed her wrist, prying the cellphone from her hand.  ``Stop.''



``It's our only option.''



``\emph{What's} our only option?''



``\emph{Buying time},'' Tattletale said.  She wrenched her hand free, but Miss Militia still had the phone.



``How?''



``You could punch the last two digits, one and four, into that keypad, see for yourself,'' Tattletale said.  ``Or you could give me the phone, let me do it, and then if Vista's in there, your conscience is\ldots less muddy, if not exactly clear.''



Miss Militia turned her face toward the phone, stared at the building that loomed over Coil's not-so-secret base.



``Shatterbird-'' I started to speak, had to catch my breath, ``She's in there too.  She was talking to Noelle.  To Echidna.  Last I saw.  They might be deciding to work together.''



``I won't have a clear conscience, no matter what I do,'' Miss Militia said.  ``But I might as well own up to it.''



Miss Militia touched the phone twice.  Long, quiet seconds reigned.



``Didn't think you had it in you,'' Tattletale commented.



There was a rumble.  My bugs couldn't reach far enough to see, but they \emph{could} see the blur.  A cloud, at the top floor of the building.



Another cloud expanded out from the top of the building, one floor down from the first.



The explosions continued, escalating, ripping through the building in stages.  I couldn't even breathe as I experienced the resulting aftershock, the vibrations as the building folded in on itself, plummeting down to the construction area.



``What-'' Assault started.



There was another explosion, muffled, and my bugs \emph{were} in range for the explosion that followed.  Plumes of earth rose in a rough circle around the building, and then the ground sank.  The entire underground base, folding in on itself.  Even with the debris of the fallen building on top of it, the area seemed to form a loose depression.



\emph{Fitting for the criminal mastermind}, I thought.



``Shiiiiiiiiiiiiiit,'' Regent said, his voice reedy.



``He didn't use it on us?'' I asked Tattletale.  ``Coil?''



She was staring at what must have been a massive cloud of dust.



``He tried, sort of,'' she said.  ``His computer was rigged to blow everything up if someone tampered too much.  I found the stuff when I went looking for his files, as I moved in.  Scared the pants off me when I realized that it was already in motion.''



``Before that?''  I asked.  ``When we were waiting for the meeting?''



``Couldn't afford to let `Echidna' loose,'' she said.  ``And I think I would've known.  Can't say for sure.''



It took minutes for everything to finish settling.



``Containment foam on the wreckage!''  Miss Militia shouted.  ``I want cape escorts for each truck and equipped PRT member, do not engage if you see her!''



She was rattling off more orders.  I couldn't focus enough to follow it all.



``She's not dead,'' Tattletale said, ``But we bought an hour, at least.  Maybe a few.  With luck, they'll upgrade this to a class-S.  We'll get reinforcements\ldots which we'll need.''



``She's stronger,'' Grue said.  He didn't sound good.  ``You fed her.''



``Had to.  Or she would have escaped before the explosion.''



``But she's stronger,'' Grue repeated himself.



Tattletale nodded.



``Do you have a plan?'' I asked.



She shook her head.  ``Not really.  Ideas.''



``I have a few too,'' I said.  ``Not good ones, though.''



``I'll take bad ideas,'' she said.  She sighed wistfully, ``Fuck.  I \emph{really} wanted an evil mastermind headquarters of my own.  It'll be years before I can build one for myself,'' Tattletale groused.



``So impatient,'' Regent clucked his tongue.



Tattletale pushed herself to her feet.  ``The next part's going to be three times as bad.  I'm going to go see if we can scrounge up some healing.''



I brought my legs up to my chest and folded my arms on my knees, resting my head on them.  The visions I'd seen were swiftly fading into memory, but the ideas behind them lingered.  For the first time in a long time, I wasn't sure I \emph{wanted} to fight, to step up and save others.  A large part of me wanted to say it was up to the heroes, to take the unsure thing over doing it myself and knowing I'd done everything I could.



I turned to Grue.  ``You okay?''



He didn't respond.



``Grue?'' I asked.



Nothing.



I used my bugs to search for someone who might be able to give medical attention.  Everyone was milling around, active, busy.



Us Undersiders aside, there were only two people nearby who weren't active, trying to contain and prepare for a potential second attack.  Weld and Miss Militia.



They were talking, and they were looking at me.



\emph{Thomas Calvert.}  My clone had informed them.  And they'd seen our faces.





