





I wanted nothing more than to \emph{stop}, to look after Grue and lick my wounds, but I couldn't let the heroes come to one of their deeply misinformed conclusions at my expense.  Not when they were talking about murder.



It took me two attempts to get to my feet.  I didn't like looking anything less than my best when surrounded by so many people who were judging me, and I felt pretty far from my best.  My bugs formed a cloak, strategically covering me much in the way that Grue did with his darkness.



I noticed how Miss Militia and Weld went silent as I approached.  Other heads turned, but nobody moved to stop me.  If anything, they edged out of my way.  They didn't clear a path, exactly, but a number of them found reasons to walk away, shift position or avoid looking at me as I moved through the perimeter they'd formed.



For an instant, I felt like I was among the students at the school.  Only this time, instead of drawing attention, with people approaching me and bumping into me, I was pushing them away.  Instead of that incessant tolling, there was only quiet, the sound of the wind, a vehicle in the distance, and the buzzing of the insects that cloaked me.



A part of me wondered how much of that was my reputation beyond Brockton Bay, and how much was my innate creepiness.



``Skitter,'' Weld said, when I reached him and Miss Militia.



``Thank you for the rescue,'' I said.  ``I can't really sum it up in words, but\ldots it was pretty damn heroic.  I owe you.''



``Imp got in touch with me, with a message from Tattletale.  The two of them made a pretty convincing argument.  You're okay?''



I offered a curt nod.  I \emph{wasn't}, but it wouldn't do to say so.  Silence was a very effective tool, I was finding, because it spoke volumes and rarely put me into a less advantageous position.  The more I talked, the more I risked revealing just how exhausted and battered I was feeling.



``Catastrophic, was the word Imp used,'' Weld said, ``when describing just what might happen if a clone got your power without any of your restraint.  Not to mention the issues posed by the psychotic Grues.  Your clones could commit mass murder on the scale of hundreds, but his threaten to lose us the battle.''



``And we suspect at least one survived,'' Miss Militia said.



I nodded.  ``There's other capes who are just as dangerous as us.  Think in terms of the damage some heroes could do.  \emph{You}?''



Weld looked at Miss Militia.  She nodded.  ``If anything, this situation is very illuminating, in terms of how bad some parahumans might be in a worst case scenario.  There are some powers that are tame at first glance, but utterly disastrous if left unchecked.''



``I take it I have one of the tame powers?'' I asked.



``No,'' Miss Militia said.  ``I wouldn't say that.''



There was a pause in the conversation.  I wasn't going to argue with or agree with her point, and neither she nor Weld were volunteering further information.



``Your team took off your armbands,'' Miss Militia said.



``Yes,'' I replied.



``You're playing very loose within the scope of the rules, with the consequences I outlined.''



``That's somewhat related to what I came here to talk to you about,'' I said.



``Go on,'' she said.



``The clone told you things,'' I ventured.  ``I wanted to address them before you jumped to conclusions.  Or, at least, I wanted to address one major point.''



``You were conscious?''  Weld asked.



I nodded.



Weld spoke, ``I understand if your clone was lying.  Psychological warfare, creating division in the ranks.  I'd be willing to believe the clone is capable of it, in light of our past experiences with you.  No offense.  But I still had to tell my boss.''



I didn't respond right away.  He was giving me a way out.  I tried to get a sense of Miss Militia's body language, using just my bugs: her arms were folded.  It was a moment where I desperately wished I could see and get a better read on her.



I'd always hated those parts in the TV shows and movies, where everything could be resolved with the simple truth.  It was why I'd never been able to watch romantic comedies.  It grated: the sitcom-esque comedic situations which would be resolved if people would only sit down, explain, and \emph{listen} to one another, the tragedies which could have been prevented with a few simple words.



I didn't want to be one of those tragedies.



``Thomas Calvert was Coil,'' I said.  I kept my voice low enough that only the two of them would hear; I didn't need to provoke a riot.



``Beg pardon?'' Weld asked.



Miss Militia's arms unfolded.  She hooked her thumbs in her belt, silent.



``Thomas Calvert got powers,'' I said, ``The ability to create a parallel reality where he could nudge things to unfold in different ways.  He used those powers to make a lot of money with no risk, hired high power mercenaries, and then hired both the Travelers and \emph{us}.  The Undersiders.''



Miss Militia shifted position, leaning against a wall with her arms folded.  ``A lot of what you say fits with what we know about Coil, but I'm not seeing where Thomas Calvert comes in.''



``His power meant anyone working under him could operate with less risk.  Our plans were that much more likely to work, because we got \emph{two} chances any time he was able to give us his attention.  With that, we took over the city.  At that point, he'd exhausted the use of the `Coil' persona, so he staged his own death.  He staged the deaths of those reporters, rigged the whole scene and set it up so it would play out like it did.  And in the end, a body double was set to die in his place.  His hired woman gets elected mayor in the aftermath, Piggot loses her job, and Thomas Calvert becomes head of the PRT.''



``You're giving him a hell of a lot of credit,'' Miss Militia said.



``He's spent years rigging this.  If you dig, you'll probably be able to find some traces of it.  Maybe the reporters who were on the scene only started working at a certain point, after he put them in position.  Maybe you can follow the money trails.  But he set \emph{everything} up.  Think about it.''



I raised one hand, counted off my points.  ``Through the Undersiders and Travelers, he would control all illicit activity in Brockton Bay, slowly moving on to the neighboring cities.  Through his money, power and his activity as Coil, he would control local business and industry.  Most of the construction companies that are rebuilding, all of the areas that are being bulldozed and rebuilt, he owned the land, he owned the businesses.  He could do it all at a loss because he was able to get money in other ways.  He was prepared to control the government through his puppets, and he controlled the \emph{heroes} through his newly acquired position in the PRT.  All in all, he was set to have an absolute grip over Brockton Bay and all of the major aspects of the city.''



``And you murdered him?'' Miss Militia asked.  ``Your clone was telling the truth?''



``I think,'' I said, and I had to pause to get my thoughts in order, ``that this dialogue of ours is going to play out far better if I don't answer that question.''



``Because you murdered him,'' Weld said.



I didn't answer.



``I'll have to discuss this with the higher-ups,'' Miss Militia said.  ``The de-facto truce we've formed should protect you until this is all over, but I'll make a strong recommendation that you be left alone for the time being.  It might help.''



``I wouldn't,'' I told Miss Militia.



``Wouldn't what?  Make my recommendation?''



``I wouldn't tell the higher-ups.  We took off the armbands because Tattletale had a feeling\ldots complicated to explain.''



``I would \emph{really} like you to explain,'' Miss Militia said.



The problem with explaining was that it threatened to offer insight on Tattletale's power.  Worse, it might get the Chicago Wards in trouble, and they'd been decent.



Maybe changing the subject\ldots ``Tattletale had ideas that Eidolon's motives weren't entirely pure.  And I don't think they were.  When we got closer, I overheard Eidolon talking to Noelle.  He knew a few things that suggested he already knew what Coil was doing.''



``\emph{Eidolon}?'' Weld asked.



Miss Militia put a hand on my shoulder, and ushered me away from the perimeter where the heroes were walking around and getting prepared.  I was pretty sure nobody was able to hear, but I didn't object.  She leaned close and spoke an order in my ear, ``\emph{Explain}.''



This explanation was having the opposite effect I'd intended.  It threatened to get me and the others in deeper trouble.



``Do you know what Cauldron is?'' I asked.



``A rumor,'' Miss Militia said.  ``It was an idea that cropped up around the time the first major parahumans did, and occasionally a person or group will use that idea and claim some greater conspiracy or a power connection.  In every case, it is investigated and thoroughly debunked.''



I frowned behind my mask.  ``If you don't think Cauldron's responsible, how do you explain the monstrous parahumans?  Like Gregor the Snail or Newter?''



``Or me?'' Weld asked.  He was just behind us.



``Or you,'' I said.  ``I've run into too many situations that involve Cauldron to buy that it's a series of hoaxes.  The Merchants had vials that granted powers, and a suitcase detailing some contract with Cauldron.  I read some of it, before Faultline's crew absconded with the rest of it.''



``Did you actually see someone drink and gain powers?''  Miss Militia asked.



``No.''



``It's a name that's acquired enough momentum and prestige that people will occasionally use it to their advantage.  Nothing more,'' Miss Militia said.



``Then why did Eidolon say that Coil was involved with Cauldron, and that \emph{Cauldron} was responsible for Noelle?''  I asked.



Miss Militia pursed her lips.  ``I don't know.  It could be that you're lying.''



``If I was going to lie, I'd pick something more believable.''



``Or you're picking something so unbelievable that it'd take ages to sort through the data.  In the meantime, this situation gets resolved and we let you walk away unharmed.  I \emph{have} talked to my team, and I've seen your records.  You tend to do that.  Protect yourself in the present with details and arguments that would take a long time to verify.''



``I'm not looking for an argument,'' I said.  ``If you don't believe that Calvert was Coil, then that's fine.  I just wanted to put all my cards on the table.''



``Except for actually admitting to the murder,'' Weld said.



``Right,'' I said.



``Assuming we believed you, what are we supposed to do with this knowledge?''  Miss Militia asked.



``For now?'' I asked, ``Nothing.  Operate as you would otherwise.  But keep your eyes open, with this information in mind.''



``And if we do?  If we keep our eyes open, thoroughly investigate this allegation about Calvert and Coil, and we still decide to arrest you, will you agree to come peacefully into custody?''



I shook my head.  ``No.  I don't think so.''



``So it's really selfishness that brings you here,'' Miss Militia said.  ``You don't expect to change the way you operate, and you expect to get away with acknowledging that you murdered a man, if not outright admitting it\ldots but you want us to change how we handle our end of things, based on your hearsay.''



``If you want to see it as self-serving, that's your call,'' I said.  ``Maybe that's how you work.  But I don't have high aspirations, now.  I saved Dinah.  I want to protect the people in my territory, and stop the forces that might hurt them, be it the Slaughterhouse Nine, Coil or Echidna.  Maybe you won't believe me when I say so, but I'm not trying to argue in my own defense here.  I won't confirm or deny what the clone said, but nothing I'm saying here really gives me an alibi or leverage to escape this situation.''



``You're giving us excuses to soften the impact of the crime you committed,'' Miss Militia said.



``I'm not admitting to anything,'' I pointed out.



``You know what I mean.''



``Maybe they are excuses, kind of.  It's one way of looking at it.  Another way is that maybe now you can maybe be more wary when talking to Eidolon, or pay more attention when you start looking into Calvert's daily life, see if anything points to Coil.  He wasn't stupid, but you don't devote that much time and energy to something without some blurring of the lines.  I don't gain much if you do that, but you could stand to benefit.''



``Maybe,'' Miss Militia said.



``Are you speaking from experience?'' Weld asked.  ``When you talk about blurring the lines between identities?''



I turned toward him, remembered that he'd seen my face.  ``That would be telling.''



``Could be,'' he answered.  ``It's something I'm interested in.  I never had the benefit of a secret identity.''



``Overrated, as far as I can tell,'' I told him.  I thought of my dad.  Was he the victim of a blurring of the lines?  Or just a casualty in a long series of events that had affected the whole city?  Or both.



``This seems like a good time to cut in,'' Tattletale said.  She approached from around the corner, turned her head in Miss Militia's direction, ``May I steal Skitter from you?''



Miss Militia waved a hand to one side, silent.



Tattletale was leading me off when Miss Militia spoke up.  ``I don't know if you're speaking the truth\ldots''



She trailed off.  I opened my mouth to speak, then shut it.  Silence was safer.



``\ldotsBut if you are, I appreciate it.  It's not like me, to demand evidence, to suspect everything, but I have to.  My teams can't afford for me to give anyone or anything the benefit of a doubt.''



``Being in charge is hard,'' I said, without turning her way.



Tattletale gestured in the direction we were going, then walked beside me as we left Weld and Miss Militia behind.  Whatever warped disease Noelle had dumped into me to weaken me and leave me unable to fight back after I'd been vomited out was steadily wearing off.  That was only a part of the overarching problems, though, and I still felt drained.  My stamina was pretty rock bottom, and the recent fight hadn't helped.  I was hungry, thirsty, and I wanted to crash for fifteen or thirty minutes.



Oddly enough, though she no doubt felt far more spry than I did, it was Tattletale who fell a half step behind me as she walked to my left, and it seemed very deliberate in how she did so.



She'd done something very similar when we'd been on the rooftop, a subtle maneuver to help portray me as the leader and as someone to be respected.  Tattletale was scary in her own way, in a very different way than \emph{I }was scary, but scary.  That she was showing deference or whichever would suggest something, even if people didn't consciously realize it.



The alternative interpretation was that she'd been hurt more in the fight than she was letting on.



``Skitter,'' Tattletale said, ``Meet Scapegoat.''



My bugs passed over the young hero, and he didn't flinch.  He would be one of the Wards, unless his stature was misleading.  His costume was a robe, though closer to Myrddin's in style than Panacea's.  My bugs traced beneath the robe to detect armor that suggested the costume was intended to be worn into a fight.  He wore a mask attached to his head by a band that felt like metal, apparently designed to flip up.  Two curling horns were attached to the band, at the sides of his forehead.



``Scapegoat?'' I asked.  ``A healer?''



``No,'' Scapegoat said.  ``But I can fix you.  Sort of.''



``What do you mean by `sort of'?''



``What I do is fragile.  It's not healing\emph{.  }You'll\emph{ }stop hurting, the wounds will disappear, but it's a delicate balance, and the duration is limited.''



``I'll take what I can get,'' I said.



``When the duration expires, unless certain conditions are met, the injuries come back.  Sometimes not as bad, sometimes worse.  And they're usually slower to heal.''



``What's the duration?'' I asked.



``Anywhere from one hour to six hours.''



``And the condition?''  I asked.



``Longer you go without breaking the effect, the better the chance the injuries \emph{stay} gone.''



``Sit,'' Tattletale said.  I sat.



Scapegoat touched my hand.  I felt a wave of sensations rushing over me.  Being hot, being cold, vibrations, the feeling of different fabrics and skin contacting mine, all at once.  The feeling of my costume against my skin became intense, \emph{sharp}, even overwhelming.  I jumped and pulled away.



``It's okay,'' Tattletale said.



I nodded, gave Scapegoat my hand once again.



Tattletale explained, ``Scapegoat's effect operates on a quantum level.  He's digging through potential realities to find unhurt versions of you, versions of you that are close enough to who you are right now that everything fits together seamlessly.''



``Except the injuries,'' I said.  Sensations were rippling over me, each simultaneous, and the simple contact of my costume against my skin or the ground under my feet was so intense that it felt electric.



Tattletale nodded.  ``Except the injuries.  For the time being, he's patching you together with unhurt parts from the versions of Skitter from the other realities and other possibilities, and his own body serves as a bridge for that.''



``Is this safe?'' I asked.  I had to grit my teeth as the effect continued to intensify.



``Relax,'' Scapegoat said.  ``More agitated you are, the weaker the effect.''



\emph{Relax}.  I reached out to my bugs, trying to feel what they felt, see what they saw, hear what they heard, and displace myself from my body.  It was a method I'd tried many times before, almost meditative.



``It doesn't take much for the effect to break,'' Tattletale said.  ``A heavy impact, a new injury or a major shock.  If that happens, all the injuries come back.  Probably worse.''



I'd planned to comment on how hard it was to relax and distract myself from the sensation when the meaning of Tattletale's words struck me.



``How the hell am I supposed to fight if I can't get hurt?''



``Play safe.  And stay within a hundred and fifty feet of Scapegoat.''



I frowned.  ``I don't think I can operate like that.''



``I can stop,'' Scapegoat said.  ``If you're feeling ungrateful.''



``You're barely functional,'' Tattletale told me, ignoring him.



``A lot of it's just the way that her puke makes you feel sick.  It's wearing off.''



``You're saying you'd rather keep going the way you are?'' Tattletale asked.  ``Ribs, lungs, exhausted, battered\ldots''



``If it means being able to fight without having my hands tied, maybe.'' I said.  \emph{And not feeling like this.  }Scapegoat's process sucked\emph{.}



``But you can't fight.  Not in this shape.''



``It doesn't really matter,'' Scapegoat said.  ``It's too late to undo it.''



All at once, the sensations stopped.  My entire body seemed to vibrate like a silent tuning fork might, in the absence of the sensations.  My ears were ringing, and spots swelled behind my eyelids.



I opened my eyes, and I still couldn't see.  No.  It was different.  There wasn't a white haze.   I wiped at the lenses of my mask, and dried bile and blood flaked off, leaving them more or less clear.



I blinked a few times, then took a deep breath.



I could see, and I could breathe.



``She's fucking blind!?''  Scapegoat yelped.



I looked down at Scapegoat.  His costume was all white and gold, his mask an alabaster goat's head fixed to a golden band, his robe white, and the chain around his waist more gold, with a goat's head buckle.  He was on his knees on the ground, and the yelling had elicited a coughing fit.



``Could've sworn I mentioned it,'' Tattletale said.



``What's going on?'' I asked.



``Oh.  He takes on whatever injuries he removes from others.  The eyes you're using right now are essentially a blend of his eyes and the ones he was able to find by paging through alternate \emph{Skitters.  }Kind of.  Hard to explain.''



``How the fuck am I supposed to operate like this?'' Scapegoat rasped.  He started coughing again.



``You visit my other teammates, make sure they're ship-shape,'' Tattletale said, ``Then we accompany you, and we create a situation where you can use the \emph{offensive} effect of your power.''



``Fuck me,'' Scapegoat said.



``It's temporary,'' she said.  In a lower voice, she added, ``And I'm paying you well.''



\emph{A corrupt hero?  Or just an enterprising one?}  I wondered.



I was also wondering if Tattletale had the funds for this.  She'd just paid off Coil's soldiers, and as far as I knew, she was committing to keeping his enterprises going, but she wouldn't have \emph{all} of his funds, nor all of his contacts.  It came perilously close to emulating Coil's fatal mistake.



Other junior heroes were gathering around us, as Scapegoat continued coughing and wheezing.  The one that caught my eye at first was a girl with a flower motif to her costume, her hair pink and styled in waves like a rose's petals, which was impressive given how she'd probably just gotten out of bed before arriving.  Others included a boy in green with a sledgehammer, a guy with plate armor with fins at the side of the visor, a boy with a candle on his tan costume, and a pair I recognized as Grace and Wanton.



``Problem, S.g.?'' the girl asked.



``Hate my power, hate my power, hate it, hate it, hate it,'' Scapegoat rasped.  Wanton and Grace gave him a hand in standing.  He was still making his way to his feet when Grace turned to me.



``You're \emph{blind}?'' she asked.



``I \emph{was},'' I said.



``It happened after we parted ways?''



``No,'' I said.



She gave me a funny look.



I kept my mouth shut, deciding to let her draw her own conclusions.  She looked down at Scapegoat, and I changed the subject.  ``You're okay?  No lasting effects from Noelle?''



``Ship shape,'' she said.  I wasn't sure she was telling the truth; Grace looked a little worse for wear.  Her hair looked wet, and the fluids that Noelle had been spitting out had congealed into the cracks and folds of her costume, with colors ranging from black to red to bilious yellow.  I wasn't sure how she'd looked before, but she looked \emph{tired}.  Was it waking up before sunrise, or had she been affected emotionally?



I probably didn't look much better.  At least my costume was black and gray.  The muck wouldn't stand out.



I \emph{felt} better, though.  Enough that I felt almost euphoric.  Aches and pains I'd stopped paying attention to long ago were gone.  It did a lot to help me disassociate from the images and scenes I'd seen inside Noelle.



Tattletale might have been right.  Maybe working with Scapegoat \emph{was} necessary.  If making this permanent was an option, I was willing to do what it took to preserve the effect, keeping Scapegoat close and keeping myself in one piece.



It wasn't something I had a lot of experience in, playing safe.



``Let's go find the others,'' I said.  \emph{I didn't like how Grue was acting when I left him behind}.  ``Grace, Wanton, are you coming with?''



``The orders we got stand until we hear different,'' Grace said.  ``We're supposed to accompany you.''



``Good.  Then let's see about getting Bentley and putting him on the dog's back.''



Tattletale shook her head.  ``Too many impacts, with him lumbering around like he does.  Either you or he take too heavy a hit, and we're back where we started.''



``What if we find a containment van and put him in the passenger seat?'' I asked.



``The last van didn't fare too well,'' Tattletale said.



``We'll use containment foam to keep him safe and in one piece if we have to,'' I told her.  ``I hope it doesn't come to that.  Let's go.''



I started to move to pick Scapegoat up off the ground, but Tattletale stopped me, putting one hand on my wrist.



``Treat yourself like you're made of glass,'' she said.  ``No heavy exertion, don't get hurt, don't strain yourself.''



``That's a little extreme,'' I said, but I didn't touch Scapegoat.



It took two people to help Scapegoat to walk.  Grace walked on one side of him, Tattletale on the other.  When he'd taken on my injuries, had he received a more crippling variation?



I was hungry to observe and absorb every tidbit of information I'd been missing.  I could see the heroes gathered, all eyes on the wreckage of the building.  PRT officers were treading the perimeter, spraying volumes of containment foam onto the rubble.



Eighty heroes, if my bugs were counting right.  Maybe eight in all were in the air.  It made it easy to find Eidolon.  Like Grace, his costume had been tinted by the film of dried fluids.  He was a few stories above the ground, and his cape flapped around him in the strong winds.



It was hard to make capes look good.  They had a way of clinging to the body, or flowing the wrong way, getting caught around an arm\ldots it took a measure of \emph{majesty} to make it work.  Eidolon could pull it off.



Ironic, that the slang for a parahuman was `cape', and so few of us wore them.



I'd worn a short cape, not so long ago, barely long enough to reach the small of my back.    I'd adopted it more for utility than style, to give me more concealed area to hide my bugs and for the marginal extra protection it afforded me.  I didn't have it now, and I was somewhat glad.  I might have felt more self-conscious, seeing Eidolon up there.  I'd wind up worrying if I really had the ability to make it look good, when I needed to focus on projecting confidence.



There weren't many villains here, and now that I could see, I was getting evidence to my previous concerns about being watched.



We reached the Undersiders, and I knelt beside Grue.  Imp was beside him, and both Regent and Bitch were standing nearby.  Regent gave me a nod, and I nodded back.



``Sorry to do this,'' I said.  I looked at the three heroes that had accompanied us, ``But I'd like to have a private conversation with my teammates.''



The bugs flowed from my costume and the surroundings, forming a moving curtain that separated me from Grace, Wanton and Scapegoat.  I gradually widened it, forcing them to back up.



Wanton let Grace support Scapegoat and tried to venture forward into the swarm.  He snorted and backed up as bugs crawled into his nose, ears and mouth.  I gave him a few seconds to experience the sensation, then removed them.  He didn't try a second time.



``What's going on?'' I asked, keeping my voice low.



``He's gone quiet,'' Imp said.  ``Not responding much.  He flinched when I tried to touch him.''



``Being inside Echidna, you see things,'' I said.  ``Variations on your trigger event, or ugly moments from your life.''



``Oh,'' Imp said.  ``\emph{Oh.}''



I looked at Grue.  He was staring off into space, with darkness gathered in thick ropes around him, to the point that I couldn't make out how he was sitting.  He did that instinctively, I'd noted.  The more he withdrew into himself, suppressed his emotions, the more his darkness manifested around him.



If it was this bad, then I wasn't sure what I could do.



I knelt beside him, and even with the darkness that wreathed him, I could sense him pulling away.



``Imp,'' I said.



``What?''



``You should take him home.''



``But\ldots I can help.''



``I know,'' I said.  ``You've helped a lot already.  But he can't stay here.  Not like this.  If he relived his trigger event, he's going to need reassurance from you.''



``His other trigger event was about \emph{you},'' Imp said.  She sounded almost accusatory.



``Maybe,'' I said.  I stared into the black lenses of her mask.  ``Do you want me to take him? Because I will.  I'll leave, Tattletale can lead the Undersiders, and you can stay and focus on assassinating clones.''



She drew her knife, turned it around in her hands, as if she were considering it.



``Whatever you do,'' I told her, ``Make the call fast.  If you aren't staying, I want to get moving fast.  I need to collect bugs before the fighting starts up again.''



She glanced down at Grue, then she looked at the others.  Regent and Rachel were watching us carefully.



For my part, I looked at Grue.  I wanted nothing more than to walk away.  I'd be okay being partially blind, waiting weeks or months to see if maybe my senses came back, if it meant holding him, helping him through this, giving him whatever support he needed so badly.



I could so vividly recall the vision I'd seen of Mannequin, and all the people I'd cared about struggling to get to safety.  Everyone had been counting on me, and I'd been failing them.  Odd, that the recollection was somehow reassuring to me in this brief moment.



In the same moment, I turned to Imp and Imp turned to me.  The black lenses of her mask met my yellow ones straight-on.



``You're the leader,'' Imp said, and that was answer enough.



I reached out and took Grue's hand.  He flinched, trying to pull away before I got a firm hold.  I managed it anyways, seized his hand between mine.



``Grue,'' I said.  I kept my voice firm, but quiet.  ``It's Skitter.  Taylor.  I need you to listen.''



He didn't budge an inch.  I squeezed his hand.  ``Listen.  You're going with Aisha, understand?  I think I know the kind of thing you saw.  What you experienced.  But you need to remember the important part, okay?  You didn't fail.  You did what you wanted to.  You saved her, you saved me, and you saved \emph{yourself}.''



He tugged, trying to pull his hand away, and I held fast.  The darkness was swelling around him.



``There's only one more part left.  Just like you did then, you need to walk away.  Leave the scene behind.  It's the best thing you can do.  You turn your back, and you walk away from where all the ugliness happened.  Understand?  Go with Aisha.  You two go home together.''



I stood, and I pulled on his hand at the same time.  He resisted.



``Take her home,'' I said.



This time, when I pulled, he worked to climb to his feet.  I took his hand and placed it firmly in Aisha's.  I watched them walk away, hand in hand, and when I couldn't see them with my eyes, I sensed them with my power, followed the movements with the blotchy vision of my bugs.



The bugs I'd formed into a barrier drifted in my direction and congregated on me.  The younger heroes were a short distance away, and Tattletale was with them.



They were watching as reinforcements arrived.



Alexandria and Legend had joined Myrddin, Chevalier and Eidolon.



The big guns.  We were finally treating this like a class S threat.



When I approached Tattletale, the other Undersiders followed me: Regent and Bitch with a litter of dogs of varying size trailing around her, chains clinking where they were attached to collars and harnesses.



Tecton was on the other side of the crowd, looking somewhat worse for wear.  Grace and Wanton started making their way toward him, and I followed by necessity, because they were helping a blind Scapegoat hobble along.



Our trip led us past the collection of major heroes, and the crowd that had gathered around them.  Glancing at them, I could see Tattletale in my peripheral vision, a smile spreading across her face.



I felt a moment's trepidation.  I'd seen that kind of smile, had seen it on Emma's face, often enough, just before she pulled something.  It wasn't directed at me, though.  I reached out for Tattletale's arm, but she was already speaking.



``Cauldron,'' she said.  The word just loud enough for the heroes to hear.



Eidolon managed to feign ignorance, not even moving a muscle, and Alexandria barely moved, nothing out of the ordinary for someone who'd heard a voice calling out.  Legend, though, turned our way, looking straight at Tattletale.  His lips pursed a fraction, and then he looked away.



Tattletale's grin widened a fraction.  She murmured to me, ``All three know.''



\emph{In which case we just added three people to our list of possible enemies.}





