





I could see the dirty looks from the heroes around us.  Tattletale's outburst would cost us something in the here and now, and I wasn't sure there was anything to be gained long-term.  Meanwhile, we were the only real villains that I was aware of, surrounded by people who didn't trust us.  People who \emph{expected} us to try something.



I was acutely aware that the Chicago Wards and Scapegoat would be listening in if I said anything to Tattletale, and the thing I most wanted to say to Tattletale would be the worst thing to say on a lot of levels.  Calling her an idiot made us look less cohesive as a team, and she never reacted well to it.



I didn't want Tecton, Grace and Wanton to hear, so I put one hand on Tattletale's shoulder to stop her, and spoke just above a whisper.  ``That was ill-timed.''



``Only opportunity I was about to get, with all of them together,'' she said.  She didn't bother to lower her voice.  ``Big piece of the puzzle, knowing this much lets me start working out how everything fits together.''



``I know,'' I murmured, ``But it wasn't a good moment.  We don't need to make enemies of the Triumvirate, and we don't need a kill order put on our heads.''



``Miss Militia wouldn't really,'' Tattletale said.



``That so?'' I asked.  ``Or is that another one of your educated guesses?''



``Educated guess,'' Tattletale said.



``Let's not forget that there's other capes with a reason to hate us, and provoking their bosses might motivate them to get on Miss Militia's case about that kill order and cleaning up Brockton Bay.  If an order comes down from above, it doesn't matter if she's willing to kill us or not.  Let's do our best to avoid seeming dangerous.''



``Sure,'' she said.  ``Got what I wanted anyways.''



I wasn't sure I was happy with that outcome.  She wasn't saying she wouldn't do it again.  ``Keep in mind that we're tired.  It's easier to make mistakes.''



``I get it.  It's cool,'' Tattletale said.  ``But just like you need time to get your bugs together, I need background info to work with before I get into a fight.''



``That's not a fight we want to start right now,'' I said.  ``Maybe ever.''



``I have ideas.  Trust me a little,'' she said, smiling a touch.



I frowned behind my mask, then led the way to the Wards.  I couldn't be lecturing her about picking her battles if I didn't do the same, and arguing this point with Tattletale wasn't going to help us right now.  Something to address another time, another day.



``What's going on?'' Tecton asked.



``Discussing strategy,'' I said.  ``How are you guys?  Wanton?''



``Myrddin caught up with me, collected all the radioactive stuff,'' Wanton said.  ``My other form feels a little weak.  Might be that my real self is feeling drained, might be that whatever powers my other self is.''



``And Raymancer?'' I asked.



Wanton glanced at Tecton, but he didn't respond.  I could tell from their body language.



``I'm sorry,'' I said.



``Nausea, vomiting, headaches, weakness\ldots and even if he makes it through today, it's probably going to kill him in the next while,'' Tecton said.



``There's healers,'' I said.  ``Tinkers who understand radiation.  I'm sure they've got good doctors looking after him now.  If you'll accept my saying so, I'd say your priority is here, now, \emph{this} situation.''



Tecton shifted position, straightening his back so he stood a little taller.  With his power armor, it put him head, shoulders and chest above me.



I had to admire the power armor.  Even the \emph{idea} of power armor, it was kind of scary to me.  Putting together a piece of machinery that could bend steel bars and punch through concrete was impressive enough on its own, but doing that and then climbing \emph{into }said machinery, walking around in it, knowing that a single malfunction could cause a potential catastrophic failure?  Being trapped in that armor, or worse, having it accidentally leverage that terrible strength against the wearer inside?



I was still operating like I had when I was blind.  A centipede crawled over the lens of my mask, obstructing my vision.  I willed it to move away.



Tecton wore his suit well.  He was a walking tank, wide as he was tall, a glossy rust-brown with brass highlights.  His eyes were barely visible, but I could see his eyes behind the mask, studying me.  He wasn't venturing a reply.



Had I been too forward?  Too presumptuous?



``Worrying about him is fine,'' I said, and the image of Grue sitting at the base of the wall flickered through my mind's eye, ``But the best thing you can do for Raymancer is get through this thing alive, and when you're done, you can do your job as team leader and find someone who can help him.''



``Myrddin will do that.''



``Maybe,'' I said.  ``But are you really willing to trust the well-being of your teammate to a supervisor?  Wouldn't it feel better to handle it yourself?''



``Unless I have reason not to, I'll rely on Myrddin and I'll feel better doing that,'' Tecton replied.  ``All of this, this whole scenario, the organization of it all, it doesn't work unless there's a measure of trust.''



``Okay,'' I said.  His reply had caught me off guard.  I hadn't expected Tecton to have that kind of faith in his superiors, and I couldn't be sure if it was my own bias or naivet\'{e} on his part that were at fault for this gap in understanding.  Even if I were right, though, it wasn't my place to `fix' him.  ``You lead the way you have to.  Sorry to make assumptions.''



``S'okay,'' Tecton said.  ``Doesn't matter if you do or not.  I'll just keep making sure you and your team don't create trouble.''



``Which we didn't do, when we lost the armbands and let them move on Eidolon,'' Grace pointed out.



``I'll take the flak for that,'' Tecton said.



``I mentioned it in passing to Miss Militia,'' I said, ``Better that you tell the truth and say we pushed hard for it.  Blame me.''



``No,'' Regent said, ``Blame \emph{me}.''



I shot him a look, and he shrugged.  ``Just wanted to get in on the fun,'' he said.



``You want me to put the blame on you, even if it means you get the kill order?'' Tecton asked.



``I'd rather not get the kill order,'' I said.



``And I'd rather not be indirectly responsible for your death,'' Tecton said.  ``I think that settles that.''



\emph{Maybe that's for the best, }I thought.  ``Then let's talk strategy and priorities.  Tecton, do you need anything?  Gear?  Time to prep?''



He shook his head.  ``No.  Need time to clean my armor and make sure it's all in working order, that's all.''



``Bitch,'' I said.  ``The dogs are okay?''



``They \emph{weren't}, but they're getting better as they grow.''



I looked at the dogs.  They were each about twice their usual size, rippling with interior and exterior muscles, layered in calcified skin and sporting bone hooks.  They were walking, which was good.  I looked over the rest of the group, trying to take in all the variables.  ``Regent, you have a bead on Shatterbird?''



``Sorta did, felt too shitty to do anything with her after metal boy yanked me out.  Around the time I started feeling better, she disappeared.''



``What does that mean?''



``She's out of range, she's dead, or she's inside Noelle.''



``Inside Echidna.  That would be bad,'' I said.



``And plausible,'' Tattletale said.  ``She \emph{would}, just to fuck us over.''



``Any idea what variants we could expect on her power?''  I asked.



Tattletale was combing her hair free of gunk with her fingers and fingernails.  ``No.  Seems like there's always a consistent factor, and the variations work off of that.  For Vista, it was space warping.  For Grue, darkness.  With Shatterbird, there's three strong possibilities: glass, sound or macrokinesis of some type.''



``Fuck me,'' Tecton said.  ``City-wide attacks with something other than glass?''



``Wood?  Metal?  Pavement?'' Tattletale suggested.  ``The way her original power works, her kinetic ability attunes other objects so they extend her range.  She reaches as far as she can, then sets up a wide-area explosion.  Instant chaos.''



``We deal with that if it happens,'' I said.  ``I can use my bugs, maybe sense if she's affecting anything besides glass, buy us time to react or take cover somehow.  But we have limited time, and we should use it.  I'd like to stop by my territory, get resupplied, and maybe swing north to wherever Coil put Atlas.''



``Atlas?'' Tecton asked.



``Skitter's giant pet beetle,'' Regent supplied an answer.



``It'll let me fly,'' I said, ``And I want to stay out of trouble until Scapegoat's power stabilizes.  Easiest to do that if I'm a hundred feet above the ground.  That's not important right now.  What I'm wanting to know is whether anyone \emph{else }has an errand they need to run.''



``Yeah,'' Tattletale said.  ``I'd like to meet up with the remaining Travelers, talk to Scrub.''



``Scrub?'' Tecton asked.



``Scrub.  And then I need to get back here to meet some guests as they arrive.  I invited Faultline's Crew.''



That gave me pause, but I couldn't say why while the heroes were here.  ``Let's find a ride.''



Half of the PRT's containment vans had turrets on the top for spraying foam, and each of those vans were circling the area where the building and construction site had been demolished and brought down on Noelle's head, laying foam down on the rubble.



The \emph{other} half were little more than mobile roadblocks, and they had been positioned to block off minor roads and alleys, leaving only a few major roads that could be protected by capes.



The benefit of having the Chicago Wards with us was that we could ask for that stuff.  Tecton went to Myrddin, Myrddin spoke a word into his armband, and a PRT agent brought our truck to us.



Tecton had been talking about organization and relying on others.  I didn't think it counted for nearly as much as he was saying.  Not the PRT, with what I'd seen and the hints at the Triumvirate's involvement.  Still, it was a ride, and I wasn't about to complain.



\blacksquare



The Travelers were in custody, with Trickster absent.  Genesis was in her monstrous form, fixed to the ground with containment foam.  I didn't see any sign of her real body, which meant she was either playing along or cooperating.  She wore a vaguely female shape with a serpent's tail from the waist down and a bony forehead that flared and swooped back behind her head like a triceratops' frill.  She had no eyes, and her mouth was wide and lipless, with tiny sharp teeth, her arms long with clawed fingertips.



Sundancer and Ballistic were glued down to either side of her, buried up to their shoulders.  Scrub was a distance away, buried up to his waist in the road.  His hair glowed with a faint red color, and a glow emanated from his eyes and the inside of his mouth.



Ballistic and Sundancer stared as we approached.  The heroes were giving them a wide berth, probably as a safety precaution.  I didn't recognize any of the three who were standing watch; a boy and girl each with shortbows and headbands with a bull's and ram's horns, and an eight-foot tall hulk of a girl with a muscular physique that had to be power-induced and a shovel broader than I was.  She was stooped over, nearly to the point of having a hunchback, and she had a severe overbite that left her top row of teeth sort of hanging off the front of her face.  Her hair was tied into thick, dark braids that hung nearly to her toes, partially obscuring her face.  Like Weld, she wasn't wearing a mask.



``Wards West!  Yo!'' Tecton called out.



The large girl turned around.  Her voice was deeper than Grue's when she spoke, ``Chicago Wards.  Not that I'm one to talk, but you're missing a few members.  They didn't-``



``Nobody's died yet,'' Tecton said, extending a hand.  She shook it.  He said, ``Got a couple sitting this one out.  Bearach put in for vacation, I think he's feeling the pressure after the Leviathan hit, and he's hoping to have a good excuse to miss the next Endbringer hit.  I told him he's not forced to come on these missions, but\ldots''



``He's compelled to defend others,'' she said.



``Yeah.  Garnett gave this one a pass.  Raymancer came, but he took a bad hit.''



``Injured?''



``Radiation poisoning.''



``How bad?'' she asked.



``Bad as it can get without killing you right away,'' Tecton replied.  ``Like I said, nobody's died \emph{yet}.''



She bobbed her head in a nod, and her hair swung in front of her.  She reached out and put a large hand on his armored shoulder.  Her voice was surprisingly gentle when she said, ``I'm sorry.''



Tecton didn't reply right away.  Sympathy could be a horrible thing to give someone, depending on who they were and how far along they were in their acceptance of the event.  I felt moisture in my eyes, but it was Grue I was thinking of.



With something to distract myself, I could deal.  I'd compartmentalize, refocus, focus on getting the job done.  But if someone gave me a few simple words and a touching gesture like this girl was offering Tecton, right here and right now, I suspected I wouldn't be able to resist losing my composure.



It was a good thing, perhaps, that nobody on my team was that type.



``I'd like to talk to the Travelers,'' Tattletale said.



The large girl looked at Tecton, and she talked to him instead of Tattletale, ``Hell of a babysitting job, Tec.  These are the guys from the news.''



``Speak for yourself,'' Tecton said, gesturing toward her captives.  ``Where's Fisherboy?''



``The captain's sitting this one out.  I'm in charge for this mission.''



There was genuine cheer in Tecton's voice as he said, ``You've been wanting that for a while.''



She smiled, which amounted to revealing more of her top row of teeth than anything else.  ``I won't get a promotion for real.  They never give them to people like me.''



``I wouldn't worry.  You're winning them over,'' Tecton said.



\emph{That camaraderie.  }If I'd joined the Wards, would I have had that?  How would things have unfolded?



``Tattletale, Undersiders, this is Gully.  I'm only as strong as I am because of the data I got from studying her power.  There was a time that she looked after two members of my team, when they were based in San Diego.  Wanton was one of 'em.  If you treat her with anything less than the utmost respect, you won't get any more cooperation from me.  Got it?''



``Not a problem,'' Tattletale said.  I nodded an agreement.



As a group, we approached the Travelers, and Gully accompanied us.



``Figures,'' Ballistic said, when we were in earshot.  ``I run to the rescue, all for nothing, and I get arrested.  No help from you guys, and Trickster fucks us \emph{all} over.  And when all's said and done, you guys are free and I'm fucking sitting here in a puddle of goo.  Tell me Trickster got his, at least?''



``Not that I'm aware,'' Tattletale said.



Ballistic sighed.



Sundancer wasn't moving.  She sat in a hunched-over position.



``Is she okay?'' I asked.



``Of course not.  Motherfucking \emph{Trickster} teleported the two of us into the sky, let us drop.  When I stood up again, he did it a second time.  My wrist and legs are probably fractured, her legs aren't any better.  She's out cold.  We need fucking medical attention, and they stuck us in this foam instead.''



I turned around.  ``Tecton, Gully, is there a way we could arrange some care for these two?''



``I'll pass on a message with my armband,'' Gully said.  ``See what the higher-ups say.''



``Might help to mention that these guys are heavy hitters at the upper end of the scale.  Sundancer can probably finish Noelle, given an opportunity, and Ballistic can definitely slow her down.''



``Will do.''



She stepped away, retrieving a smart phone from her pocket and putting it to one ear.



``You'd think she'd wear a mask,'' Regent muttered.  I sent a collection of bugs flying at his face and shot him a dirty look at the same time.  He was left sputtering.



Ballistic stared up at me.  I couldn't see his eyes through the lenses of his mask, but I was acutely aware of his silence, here.  He wasn't offering thanks.



``Well,'' Tattletale said, ``Let's see if my guess is right.  If not, I wasted a lot of money and a lot of thinking time on this problem.''



``Guess?'' Tecton asked.



``Guess.''  Tattletale briskly walked in Scrub's direction.  The ex-Merchant was buried in a standing position, three-quarters of his body sunken into a hole in the ground roughly two and a half feet in diameter.  He couldn't raise his arms up out of the hole to pull or push himself up, and the narrow confines of the hole didn't let him bend his legs.



A flash marked an explosion nearby, hitting only air.



``Scrub,'' Tattletale said.



Scrub didn't respond.



``So you don't talk,'' she said, ``That makes this harder.''



She sat down cross-legged, to put herself on more of a level with him.   A flash erupted two feet away from her, a few feet off the ground, and was followed by a slight movement of the air, stirring Tattletale's blond hair.  She brushed it back into place with her hand.



``What's the guess?'' I asked.



``His power.  What do you think it is?''



There was another flash.  Again, it hit only air.



``I was thinking uncontrolled annihilation blasts, but you're going to tell me it's something else,'' I said.



``I am.''



Another flash.  Tattletale drummed her fingertips on her knee, watching, waiting.



``We're kind of on a schedule,'' I said.  ``So maybe hurry up with the explanation?''



``I'm just waiting.  It's a matter of time before I can check my theory.  If it's checkable.''



``\emph{If} it's checkable?''



``Can't you just play along?  I love those `murder she wrote' moments, where I can pull everyone together, then dish the info.  Everything makes sense, the puzzle pieces fall together, and things start falling into place.  We lose all the effect if I reveal some of it early.''



``And we lose that opportunity if you sit too close to the guy with the uncontrolled power that \emph{isn't} energy blasts, get half your face scooped off and die,'' I said.  ``I know you know you're safe, but let's be \emph{extra} careful.''



I extended a hand, but Tattletale didn't take it.  \emph{Right, Scapegoat's effect}.  She stood without my help, then stepped back.



``I'll explain this part of it once I verify,'' Tattletale said.  ``The rest has to wait until Faultline's people fly in.''



``How long will \emph{that} be?'' I asked.



``Hour and a half from the time I made the call, about.  That was about thirty-five minutes ago-``



Tattletale stopped as another flash hit.  It intersected the ground, but the ground was left intact.



``There!''  She said.  Her hand went to her belt, and she had a laser pointer out in a second.  She circled the area where the blast hit.  ``Can you remove that section of ground without breaking the middle?''



Tecton took a half-step forward, but Gully stopped him.  She tapped her shovel against the ground, and the area in question rose from the ground, perfectly cylindrical, three feet high.



Another of Scrub's explosions struck, and a spherical gouge was cut out at the bottom of the pillar.  Tattletale ducked close, grabbing it as it toppled, then hurried back out of Scrub's range, dragging the column after her.



``Careful!'' I told her.  ``If you'd been hit-``



``Doesn't matter,'' she said.  She rested the cylinder with the vaguely pointed bottom down on the ground, tapped her finger on the top – what had been the road's surface.  ``Look.''



I peered closer.



It was so subtle I almost missed it.  The texture of the road's surface was interrupted, shifting minutely to a different texture and fractionally different shade.  The area formed a neat circle.



I stood back while the others looked.  Only Rachel didn't investigate.  She was more focused on her dogs, using a metal-tined comb to brush their fur clear of gunk.  Bentley nudged my hand, and I gave him a scratch on the crown of his head.



``I don't get it,'' Tecton said.  ``The blast \emph{changed} it?''



``The blast \emph{transplanted} it,'' Tattletale said, grinning. 



``How the hell do you even notice something like that?'' Wanton asked, touching the surface.



``That doesn't matter.  Now, if everyone will allow me, I'd like to have my moment now.  We all know that there's built-in limitations to our power.  These limitations are apparently for our benefit, even if we might not always \emph{love} them.  The Manton effect is a big one.  We get powers, and in the moment those powers take hold, we get some hardwired restrictions that keep those powers from hurting us.  A running theory says that it goes too far, and overgeneralizes to humans or living things who aren't \emph{us}.  Another says that it's just our empathy at work, that we have built-in limitations because we care about our fellow human beings, and our powers acknowledge that.  With me so far?''



``I'm listening,'' I said.



``There's other limitations or advantages that come with the powers.  Sundancer over there can't be burned.  Temperature completely and one hundred percent normalizes within a certain range of her body.  Our old buddy Shadow Stalker could pass through surfaces but never sank into the ground and fell to the center of the Earth.  And Scrub here, with his uncontrolled power, never blasts the ground out from under his feet, and he's far less likely to collapse a building onto his own head by accidentally destroying a critical support.  Why?''



Nobody volunteered an answer.  Tattletale smiled.



She explained, ``Looking at this, I'm thinking it's because the same \emph{passengers} that give us our powers are connecting us to some other parallel Earth.  Maybe even individual \emph{collections} of Earths for each of us, so that there's no ugly interactions when two powers meet.  Scrub here shunts matter into an Earth where there's architecture roughly corresponding to our own, but he won't tear up his own footing because he's shunting in the more permanent elements as his power shunts stuff \emph{out}.  When Shadow Stalker displaces her mass, she displaces it into another Earth, distributing her mass and her footing across the two worlds.  She's still\emph{ all }\emph{there}, she's just not all \emph{here}.  And when Sundancer superheats her immediate area, she's doing what Scrub does, and shunting a roughly human-shaped patch of superheated air and fire into a parallel Earth, shunting room temperature air into her immediate surroundings.''



``Doesn't that mean that they'd be causing destruction in some hapless world?'' Wanton asked.



``Good question.'' Tattletale grinned.  ``Yes.  Probably.  Could be that every time Sundancer's power protects herself, she's setting the approximate location of her other Earth on fire.  Nothing's saying that other Earth is \emph{populated}, but it could be.''



I shivered.  It was too much to think about.  ``Does that apply to other powers?  Mine doesn't really protect me.''



``Ah,'' Tattletale grinned.  She raised a finger, ``But here's my question to you.  What's your power source?  Where are you getting the energy you use to relay and receive information from your bugs in real-time?  Keep in mind that so far, the only person who's been able to intercept, understand and replicate your signals has been \emph{Leet.}``



``You're saying that when I got my powers, my passenger picked a suitable Earth, and I've been\ldots what?  Leeching power from it?''



``Possible.  Or drawing power from two hundred or two hundred \emph{million} Earths.  Maybe it's ambient light and radiation, and you're condensing that energy into something you can use.''



``Am I hurting or killing people?'' I asked.



``Who knows?'' Tattletale shrugged.  She flashed me a smile.  ``Maybe your passenger picked a few barren Earths with no people at all.  Earths where life never evolved, or where humankind went extinct.  Or maybe you're drawing a teeny, tiny bit of energy from millions of worlds, to the point that nobody would ever notice.''



``Or maybe you're turning another Earth's Brockton Bay into a cold, barren wasteland,'' Regent commented.



\emph{Don't want to think about it, }I thought.  It wasn't like I could even turn my power \emph{off}, short of killing myself or removing every bug from my vicinity.



``It's\ldots a bit of a leap,'' Tecton said, ``To go from looking a piece of pavement to thinking on that scale.''



``It's only a theory, but I've been giving a lot of thought to powers in general, and my teammates know I'm pretty good with this stuff.  Now, I want you to imagine \emph{this}.  Think about all the complex processing and work that goes into managing powers.  Hell, Skitter can individually control every insect in her swarm and \emph{simultaneously} give each a completely different instruction. My own power, it's similar.  Tecton's brainpower, his processing as he thinks about engineering, architecture\ldots where's that work taking place? \emph{ Our} brains certainly aren't capable of it.''



``The other world?'' I asked.



``But how?  Who?'' she asked.



``Tell me,'' I said.



``Insofar as we've even \emph{thought} about passengers, we've been sort of inclined to think about them as being pretty small.  After all, the way Bonesaw talked about them, they're these things that work their way into our heads, bond with our brains and then burn themselves off in the process of reconfiguring how our heads work.  Right?  But anything as small as what she's describing wouldn't possibly be able to do what we need to manage our powers.  So what I'm asking is\ldots what if they're big?  Massive.  What if each and every passenger is \emph{picking} us, for whatever reason, they find us and then they bind to us.  They connect to us by rewiring a tiny part of our tiny brains, and through that extra lobe, they connect us to all the other parallel Earths, including the one where they reside?  Maybe they're physical, maybe they're more ethereal, I dunno, they could be plant or animal, but they're \emph{there}.  Lifeforms that could be \emph{titanic}, the size of cities, continents or \emph{moon}\emph{s, }lurking in some other parallel Earth and attaching themselves to us with a thread, a fine hair that stretches across dimensions to a lobe in our brain, sending and receiving all necessary data\emph{.  }And things like that are\emph{ }connected to each and every one of us who have powers and those of us who don't, existing only to process our abilities, to absorb and channel the necessary energies, signals and information, and make each and every one of us into\ldots''



She paused to chuckle a little.



``\ldotsInto superheroes and supervillains and everyday nobodies who use their powers for business or entertainment.''



I shivered.



``It's nonsense,'' Tecton said.



``Maybe.  It \emph{is} just a theory,'' Tattletale said.  ``But it \emph{feels} mostly right, and I'd \emph{love} to hear a better explanation.''



``\emph{Why}?'' Gully asked.  ``Why would they do that?  If they're that powerful, if they're that big, why care about us?''



``Excellent question,'' Tattletale replied.  She grinned. ``No clue.''



``I'm not saying it's not an interesting theory,'' I hedged, ``But how does this tie into the Echidna situation?  Is she an Endbringer, and do the Endbringers relate to the passengers?''



``Oh.  I'm pretty damn sure there's no real connection between her and Endbringers.  I saw her at work.  Nothing really \emph{fit}, as far as the various things I saw about Endbringers.  No, she's something else.''



``Then what does this have to do with her?  Because this definitely could have waited.''



``Well, there's two major factors at play here,'' Tattletale said.  ``Two plans.  Numero uno is that it's really quite possible that Echidna's got a broken passenger.  Something went wrong, it's damaged, it's demented, or some of the usual limits are gone.  Hell, maybe it's gaining more of a grip over her as she brings more of the passenger into this world to operate her body, and the usual processes that keep a passenger passive and sleeping are missing in hers.  Or it could be that her passenger is trying to make its way into our world.''



``And it's city sized?'' Wanton asked.  ``Or moon sized?''



Tattletale shrugged.  ``It's not like she couldn't get that big.  I was thinking about throwing Rachel's dogs at her until she couldn't support her own weight, but she'd still be able to use her power and puke, and while her clones seem to be getting more fragile, weaker and more plentiful as she grows, I'm not positive that's a good game plan.''



``Not fucking risking my dogs like that again,'' Rachel said.



``Of course,'' Tattletale added.  ``There's that too.  I can't really say more about Echidna without finding more about Cauldron's process for granting powers, and I'd \emph{really} like to grill the Travelers on that front.  But understanding all this is our best bet for understanding Echidna, and potentially stopping her.  Or even fixing her.''



I glanced at the others.  ``But\ldots there's some powerful people who wouldn't want us to dig for more information about Cauldron.''



``There are,'' Tattletale said.  She glanced at the heroes who were with us: Tecton, Wanton, Grace, Gully, Scapegoat and the twins.  ``Which means we may be doing this \emph{without} the support of the other heroes who are here to stop Echidna.  Which is probably sensible, because they probably won't be on board with the next idea I'm going to propose for a democratic vote.  The \emph{second} reason why I wanted to carry out this particular research project.''



``I get the feeling I'm not going to like this,'' Grace said.



Tattletale smiled, ``I think we can tear a hole between dimensions.''





