





``I was perfectly happy,'' Scapegoat said, ``Being able to tell myself that hey, the news is blowing things out of proportion.  There's no \emph{way} Brockton Bay is as scary as they're making it out to be.  Dragon suits get sent in and are promptly forced out, but really, the \emph{mayor}`\emph{s} telling Washington it's safe enough.  The media got something wrong, or they're making little problems sound bigger than they are.  See the piles of dead bodies where this girl--''



``Echidna,'' Tattletale supplied.



``Where Echidna spat out clones.  Okay.  I can live with that.  An unusual power and strong parahuman.  Could be an exaggeration.  See the destruction, the ruined buildings and the streets that \emph{still} haven't drained a hundred percent.  More or less what I expected from the news.  The girl with the mutant dogs?  Bug girl?  Still manageable.  But \emph{she} opens her mouth,'' Scapegoat pointed at Tattletale, ``And pop goes my bubble of happy self-delusion.''



``You want to tear a hole in reality?'' Tecton asked Tattletale.



``I do.  I want to use Scrub's power in conjunction with another power that draws heavily on accessing other worlds.  It's why I contacted Faultline's crew.  They're our best bet.  Myrddin might work, but he's unlikely to cooperate.  Scapegoat could work too, but I think it'd take too long, and it might need a human sacrifice, having Scrub hit someone who was heavily affected by the goat's power.''



Regent nudged me.  ``With Grue gone, it's your job to lay down the law.  \emph{No human sacrifices}.''



He'd mimicked Grue's tone of voice, with a forced lowness.



No human sacrifices?  Did I really want to veto any possibilities, when we were faced with threats like the Endbringers and Echidna?



``You're not saying no,'' Regent commented.



``Tattletale,'' I said, ``What's the point?  Why open a hole like that?''



``It's a place to put Noelle, for one thing.''



``We can stop her other ways,'' I said.  ``She's not invincible.''



``Yet,'' Tattletale said.



``Yet.  We can put her down.  With Legend, Eidolon and Alexandria alone, we should be able to do enough damage that she can't keep regenerating.''



``Maybe.  It was hard enough before.  We've got big guns, now, but it's going to be rough.  It'll be a lot easier if we have the Travelers on our side, and we'll have that if we can give them what they want.  A way home.''



``A way home?'' Tecton asked.



``Cauldron's the group responsible for plucking people from their realities, wiping their memories and leaving them \emph{changed}, marked with a tattoo,'' Tattletale said.  She glanced at Gully.



I did too.  Gully's eyes were wide behind the curtain of braids.



``And the Travelers, far as I can figure, are the same.  Only they still have their memories, and they weren't altered in appearance.  It's like Noelle got her entire group's share,'' Tattletale said.



Gully slammed her shovel into the ground, but she didn't say anything as seconds passed.



``You want to tear a hole in reality to send them \emph{home}?'' Tecton asked.



``It's the best bargaining chip we have, short of a cure for Noelle.''



``How do we even know which world it is?''



``We don't, but we can ask,'' Tattletale said.  ``What I'm getting at is that this is our best weapon, our best bargaining chip and our best tool.  If I'm right, if I\emph{`}m \emph{close} to right, then this is a way to shut powers off at the \emph{source}.''



``Assuming you have a way to kill or break the connection with these things you're describing,'' Tecton said.



``I'm assuming we can get our hands on some weapon of mass destruction,'' Tattletale said.



``Too many potential disasters,'' Tecton said.  ``Listen, I get it.  I've been where you are.  There's a lot of tinkers and some thinkers who've been where you're at right now.  Who've had that brilliant idea with the power to change the \emph{world}, for better or for worse.  Most of us stop at that line.  We have to.''



``This isn't changing the world,'' Tattletale said.  ``This is going to the \emph{heart} of every single damn problem we've been facing and surgically removing the most dangerous parts.  We can access the places where the powers are coming from and shut them off.  It's an \emph{answer}.''



``\emph{If }you can manage the risk,'' Tecton said.  ``And I don't think \emph{surgically} is even close to being the word you want.  With tears in reality, it's equivalent to using explosives with a yield you can't even guess at.''



``I'm a good guesser,'' Tattletale said.



``And this is the part where I cut in,'' I said.  ``We're short on time, and I have stuff to see to.  Why don't you guys talk this through, and I'll collect supplies with Scapegoat in the meantime.''



``Go for it,'' Tattletale said.



``I'll come,'' Rachel told me.  ``Too much fucking talking.''



``We can't let Scapegoat leave in the company of two known, dangerous villains,'' Tecton said.



``Send someone with us,'' I said.



``Gully and Wanton, then,'' Tecton said.  ``If that's alright, Gully?  We'll watch your prisoners.''



``I'll ask,'' she said.



``Thank you,'' I said.



``Atlas isn't far from your territory,'' Tattletale said.  ``Head a little north, and you should find him with your range.''



I nodded.



Gully gave me a thumbs up, her phone still pressed to one ear, and we headed to the van.  Wanton was the only one who could fit in the driver's seat and who had a license.



With Gully and Bitch both in the back, I figured it would be safest to ride with them.  Rachel was managing better these days, but a fight between her and one of the heroes could spell disaster.



It took a minute for all the dogs to climb into the back of the vehicle.  I used the time to gather my bugs in nearby buildings, where I could collect them on my return trip.



Rachel wasn't feeling talkative, Gully seemed lost in thought, and both Wanton and Scapegoat were in the front.  That left me to get a discussion going, and I was too tired to bother.  I closed my eyes, arranging my bugs into an arrow on the dashboard of the van.  They rearranged themselves into a right turn sign to steer him toward Lord street, and from there it was relatively smooth sailing.



Someone had given the order for evacuation, and people were being directed to the shelters.  We had only two indications that things would get any worse.  Tattletale's gut, which wasn't a sure thing, and Dinah, who'd indicated that there was a good chance a large portion of the city would suffer at Echidna's hands.



Or, even, not specifically at her hands.  With our luck, it would be Tattletale's plan that leveled half the city and we'd find out that Echidna was permanently trapped beneath the rubble, not even a consideration.



Twice, I nodded off, my head starting to drift forward, before the sudden movement of my bugs stirred me fully awake.  The interior of the van was warm, dim and the vibration was oddly soothing.



The third time I drifted off, my bugs didn't catch the movement.  My head leaned back against the wall of the van, and I slipped into the twilight state of near-sleep.



It was the appearance of Atlas that brought me back to my senses.  I signaled for Wanton to stop the van.



He was inside a garage, so still I thought he might be dead.  Without ingrained instincts, he had only the barest minimum of processing.  Enough to breathe, at least.



He hadn't eaten in twelve hours.  I was sure to feed him a supply of the less essential bugs from the area, moving them straight into his open mouth.  I could reach my lair, and drew out every single one of the bugs I had stored there, calling them to me.



He would be weak, I noted, but at least he wasn't hurt.  Coil had probably ordered for Atlas to be left alone for much the same reason that he'd carted the giant beetle to this area.  Doing otherwise could have clued the other Undersiders into what was really going on.



Wanton opened the back of the van, and I stepped outside.  Gully emerged as well, likely due to curiosity as much as anything else.



Atlas, at my bidding, found his way past the closed and unlocked door, made his way outside and flew to me.



When the giant beetle dropped out of the sky to land just beside the van, Wanton briefly shifted into his other form, and Gully raised her shovel protectively in front of her.



My bugs flowed over Atlas' carapace, and I used my hands as well, checking there was no damage.  Scrapes and gouges on his underside.  Had they lifted him into a truck to transport him?  My gloved fingertip ran along the length of his scythe-like foreleg.  Maybe I needed to take the time to give him more care, sharpen the natural weapons, tend to his shell\ldots



I blinked a few times.  I was tired, and my lack of focus was dangerous.  Time was short.



``Are your dogs well enough to run?''  I asked Rachel.



She was still in the truck, sitting on one of the benches that were built into the side.  She hopped down to the street, the dogs milling around her.  ``Probably.''



``Then let's go,'' I said.  I stepped onto Altas' back, but I didn't take a seat.  I let him rise into the air, and I drew all the bugs in the area to me.  I didn't settle into a sitting position until I was obscured from view.



I couldn't move too far away from Scapegoat.  I was tethered to him by an invisible, intangible cord, about one hundred and fifty feet long; about half a city block.



Still, provided I was directly above him, it let me fly about eight or nine stories above the ground.  I wasn't \emph{untouchable}, but I was safer.



``\ldotsHear me,'' Wanton spoke.



My bugs spelled out the word `yes'.



``Creepy,'' he said.  ``I need \ldotsrections.''



There were two possibilities that sprung to mind as far as what that last word might be.  I guessed it was `directions' and pointed him back to Lord street.  I wanted as many of the good bugs as I could bring, but I was limited in how many Atlas could carry and I doubted the others would be keen to see them packed into the back of the truck.



Instead, I drew out lines of thread, ferried the slower moving bugs onto my back, and loosely bound them.  Bugs strung out on silk cords, like kindergarteners did with popcorn on thread.  The rest found shelter in the folds, compartments and creases of my costume.



I kept close to the ground as I followed.  Had to stay close to Scapegoat and I couldn't trust that Atlas had enough energy to carry me until we'd flown a bit and I could see how his stamina was.



My hair and the tatters of my costume flapped behind me as we flew, clumped together in parts with the fluid that I'd been soaked with while inside Noelle.  I had bugs crawl over both to devour and separate the worst of it.  The ones on the threads that trailed behind me with the faster flying insects were surviving, which was key.



The little tasks kept me awake, if not entirely focused. I was caught off guard when I let the van miss a turn.  If a good shot of adrenaline didn't wake me up, I might be at a disadvantage in the coming fight.



I got that kick of adrenaline sooner than I'd wanted.  We reached the clearing where the others had been and found it empty.  The Travelers, Tattletale, Regent, Scrub and the heroes were gone.



I landed, and the van doors opened.  Bitch stopped just beside me, Bentley at full size and the other dogs standing maybe three feet tall at the shoulder.



``Gully, you have an armband.  Have the heroes communicated anything?''  I asked.



``No.''



``Can you do me a favor and see if anyone has answers on where Tattletale and the others are.  For now, we should head back to the perimeter.''



``You're giving orders?'' Wanton asked.



``Consider it a suggestion,'' I said.  Gully had been pleased at the semi-promotion, with being put in charge.  I could concede to let her call or confirm the shots if it kept her happy.  ``It's Gully's choice.''



She glanced at me.  ``It's sound.  I'll use the armband while Wanton drives.''



We reached the perimeter around the destroyed building before she got a reply, and we found Tattletale in the company of some of the major heroes.  Legend, Alexandria and Eidolon weren't present, but that wasn't a huge surprise.  They apparently had secrets to keep.



More than one cape turned their attention to me as I approached.  They didn't shoot, though.  I was relieved at that.  It would be a bad way to go, getting gunned down out of the air by heroes with twitchy trigger fingers.



I had to pause while the van stopped to pass through a contingent of heroes.  Rachel sort of strode through without really asking for permission.



It wouldn't be winning us any points with the good guys, ignoring courtesy, but the fact that Tattletale and Regent had disappeared from our rendezvous spot and that they were now in the midst of a group of twenty-seven heroes.  They weren't at gunpoint, not really, but the implied threat was apparent.



I waited until Scapegoat was out of the van and hobbling toward the crowd before bringing Atlas in for a landing.  I rose to a standing position so I wouldn't be sitting down when the bugs parted to reveal me.



``What's going on?'' I asked.  My bugs passed through the crowd, not getting in anyone's way, not touching on faces or bare skin where I could help it, but giving me a way to track everyone nearby.



It was Tecton who answered me.  ``Tattletale wasn't willing to drop her idea.  I suggested taking it to our superiors, and she agreed.''



``It's too dangerous,'' Myrddin said.  He stood by with Miss Militia and Chevalier beside him.



``It's our best option,'' Tattletale said.



``It's a plan that puts everyone involved at an immense degree of risk, and it costs us time we don't have.''



``We have a \emph{little} time,'' Tattletale retorted.  ``I don't see any movement there, do you?''



``We can't even guarantee it'll work,'' Myrddin replied.



``Are you saying that because you consider yourself the resident dimension manipulator or because you're afraid it'll lead to a big revelation about Cauldron?''



I could have imagined it, but I could have sworn my bugs were aware of a collective intake of breath.  Not everyone present, not even one in five\ldots but people did react.



How far did this reach?



``What are you talking about?''  Myrddin asked.



``No?  I'm not seeing anything from you.  Guess you're in the clear,'' Tattletale replied.



``Tattletale,'' Miss Militia cut in, ``This isn't the time for games, making accusations in the hopes of finding information.''



``I agree,'' I said.  ``Stick to the topic at hand.''



``It's not a game,'' Tattletale said.  She looked at me, and she wasn't smiling.  ``And I don't see how we can discuss it if we ignore the elephant in the room.''



``\emph{Try},'' I told her.



``What's going on?'' Chevalier asked.  Of everyone in the immediate area, he had the most \emph{presence}.  He wore gleaming gold and silver armor, but it was the massive, ornate cannonblade that made him so imposing, with a blade that was twelve feet long, three feet wide and capable of growing larger, resting against his shoulder as though it were as light as a feather.



``Rest assured, Chevalier, this is a discussion for another day,'' Miss Militia said.  ``One I'm \emph{definitely} interested in continuing, but not when it threatens to distract us.''



``If you're sure,'' Myrddin said.



``Trust me.  Please,'' Miss Militia replied.



``Cauldron is led or backed up by the Tr--''



Miss Militia struck Tattletale, cutting her off before she could finish the sentence.  It was only as Miss Militia dropped to her knees, setting one knee on Tattletale's throat, that I saw she'd had a gun in her hand.  She gripped Tattletale by the cheeks, pinching her mouth open, and slid the gun into her mouth.



I could sense Rachel striding forward, saw Regent moving to raise one hand in Miss Militia's direction.  My arms went out to either side of me: one to bar Rachel's advance, another to catch Regent's wrist.



``Don't be foolish, Tattletale,'' Miss Militia said.  ``Why would you risk everything like this?''



Tattletale glanced at me, then mumbled something incomprehensible around the gun barrel.  Her cheekbone was bleeding where she'd been struck.



Miss Militia looked up at me.  A gun materialized in her other hand, identical to the one that was jammed between Tattletale's teeth, but she didn't point it at me.  ``Do we have a problem, Skitter?''



``Not unless you pull the trigger,'' I said.  ``We aren't going to start a fight with this many people around.  It would be \emph{suicidal}.''



I looked Tattletale in the eye as I said that last word.



``Is she a clone?'' Myrddin asked.



``I almost wish she was,'' I replied.  ``No.  It's the real her.''



``Can you tell me why she's doing this?'' Miss Militia asked.



``I don't know,'' I said.  ``Yes, but not in entirety.''  We were tired, but that wasn't it, it wasn't \emph{all} of it.  Couldn't be.  It wouldn't account for the almost suicidal edge to her actions in just the last half hour.  There was something else going on.



``Tattletale,'' Miss Militia said, ``I'm going to remove the gun.  Think \emph{very} carefully about what you say.  Deliberately attempting to divide our ranks could be seen as a violation of the truce, and I \emph{will} push for the kill order if it goes that far.''



Tattletale nodded.  She winced as the gun was removed.  ``You can't put a kill order on the other Undersiders.  They aren't responsible for anything I'm saying.  Heck, two of them aren't even \emph{here}.  You'd be killing innocents.''



``I don't think anyone here thinks any of you are innocent,'' Miss Militia said.



``They're \emph{relative} innocents?'' Tattletale tried.



``Quiet,'' Miss Militia said, her voice tight.



``I'll be quiet when you tell me you won't punish others because of me.''



``Just be quiet,'' Miss Militia said.



``M.M.,'' Chevalier said, his voice low, ``I won't gainsay any of your decisions, and with this being your city, you have the say unless one of the Triumvirate supercedes your order\ldots but you're attacking a girl when she was only talking, and there are a lot of eyes and ears here.''



``You're saying it doesn't look good,'' Miss Militia said.  Her eyes were fixed on Tattletale.



``Not for your career.''



``I don't give a flying fuck about my career,'' she replied.  ``I care about all of us getting out of here in one piece.''



``And you think she'll put all of us in danger if she opens her mouth?'' Chevalier asked.



``Yes.  I think Tattletale can do a \emph{catastrophic} amount of damage if she opens her mouth,'' Miss Militia said.  ``You've read her file.''



``I have,'' Myrddin said.



``Is the information she wants to share pertinent to this crisis?''  Chevalier asked.



``Not immediately,'' Miss Militia said.  Tattletale cleared her throat, apparently asking for permission to speak, but Miss Militia gave her a tight shake of the head in response.  ``Not as far as I'm aware.  I've discussed much of it with Skitter.''



``If I may,'' I spoke up.  Innumerable sets of eyes turned my way.  I let go of Regent's hand and dropped the hand that was still held up in front of Rachel.



``What is it?'' Myrddin asked.



``I can try to explain.  You can send away the rest of the capes, I explain to you three, and you decide if and how much information to disseminate to your underlings.  I'll try to be more delicate than Tattletale was, avoid the more sensitive parts.  I don't agree with Tattletale's plan, but it's too dangerous to make calls without knowing the key details, and some of this stuff is need-to-know, if we're to have any chance of getting the Travelers or Noelle to cooperate.''



Myrddin looked at Miss Militia, and she nodded.



Myrddin raised his voice.  ``I'd like everyone who isn't \emph{immediately} involved in this discussion to find something else to do.''



Some people started shuffling away.  Aside from heading straight towards the site where helicopters were still laying down containment foam or walking face first into the containment van Wanton had parked, there were only two directions to walk, and one group of people weren't moving.



Gully.  One of the twins was tugging on her arm, but she wasn't budging.



``Gully,'' a cape I didn't recognize spoke, ``Get a move on.''



``I want answers,'' she said.  ``The Undersiders have them.''



``And Chevalier will contact me with what he feels we need to know, and I'll pass that on to you and your squad,'' the cape said.



``That's not enough,'' she said.  ``I don't want the condensed version.  I want to hear why I'm like \emph{this}.''



A murmur ran through the crowd, and I noted that some of the capes who had reacted before were standing out more.  One was breathing harder, another was fidgeting where she'd been calm before.



``This kind of insubordination is what goes on your file and costs you promotions,'' the cape said.



``I've been passed up for promotion so many times I've already gotten the message.  Monsters don't get to be team captain.  Your argument doesn't have any weight to it, Lono.''



Weld approached her.  Their eyes met, and Weld came to a stop, turning around so that he stood just to her right.  He didn't say a word.



Miss Militia stared at him, and he didn't even flinch.



``This is a critical situation,'' Myrddin said.  ``We're on the brink of another potential conflict with an S-class threat.  If the Undersiders have information we can use, information that could be sensitive, we need you to clear out.''



``I've spent years like this,'' Gully said.  ``It's not just me, either.  There're others.  Weld\ldots''



``Hunch,'' Weld added.  ``Gentle Giant, Sanguine.''



``Weld and Hunch, Gentle Giant and Sanguine,'' Gully said.  ``And the others who weren't even lucky enough to find the Wards or the Protectorate before they found themselves in trouble.  It's not just for me.  We need to know for \emph{them}.''



``This isn't the time or place.''



``With all due respect, spend a \emph{day} in my shoes, Myrddin.  Just one, and then tell me again, that I have to wait one day, one hour, even one \emph{minute} longer for an explanation.''



The ground shuddered, and I thought at first that it was \emph{her}, but she looked surprised.



It was Noelle.  Echidna.  She was active and fighting her way free.



``We're out of time.  Enough of this,'' Myrddin said.  ``Gully, Weld, join your teams.''



Gully planted her shovel in the ground, put one foot on top of the blade, and folded her hands on the handle.



``We could share with them,'' Miss Militia said.  ``I know Weld is an exemplary hero, and we could trust him to keep necessary information to himself.''



``I might agree,'' Chevalier said, ``If it weren't for the dramatic flair Gully was displaying.  I don't trust that \emph{she} will stay quiet on the subject.''



Another shudder.  Heroes were running to adopt battle lines, forming a circle around the construction lot with the ruined building.  The invincible, the power immune, masters with durable pets and forcefield makers were positioning themselves at even intervals around the circle.



``We don't have time.  Myrddin,'' I said. ``You and I can both fly.  If we go to a nearby rooftop--''



``Fuck me,'' Tattletale said.  ``So much wasted time.''



She grabbed for Miss Militia's gun.  When Miss Militia didn't let go, Tattletale took one step closer and pressed her forehead against the gun barrel.  ``\emph{Do it}.  Kill me.  You've seen a lot of people die in your lifetime.  People important to you, dying because of an \emph{idea}.  So kill me because I believe \emph{this} idea should be heard by people who care.  Close the damn circle.''



\emph{Why?} I thought.



``The Triumvirate,'' Tattletale said.



Miss Militia stared at her, but didn't pull the trigger.



``The\ldots Triumvirate?'' Gully asked.



``I'm in deep shit anyways,'' Tattletale said.  ``For saying what I already have.  We \emph{all} are.  Sad fact is, I have \emph{better }chance of surviving if it's all out in the open.  The Triumvirate \emph{is} Cauldron.  Eidolon, Legend, Alexandria.  They started it, or they're so involved in it that it's incestuous.''



``Fuck me,'' Regent muttered.



I couldn't even breathe.  I was waiting for Miss Militia to pull the trigger.



``They made me like this?'' Gully asked.  ``Why?''



``Not sure.  A warning, maybe, to people who didn't pay their bills.  Or they figured that while they were brainwashing you, they'd implant you with a built-in weakness, something a paying customer could exploit.''



``That's it?  \emph{That's} your answer?''



``I'm sorry,'' I said.  I wasn't sure if I was apologizing because it was insufficient or because I'd let Tattletale take things this far.



The ground shook, more violently than before.  The air was filled with the thrum of the helicopters that were flying overhead.



By contrast, \emph{he} flew so silently that I almost missed him setting down.  I didn't have bugs in the area, and my eyes were trained in the general direction of Gully and the wreckage of Coil's collapsed base.



Legend, landing in the midst of us.



``You heard,'' Tattletale said.  She didn't sound surprised.



``Lipreading,'' he murmured.  ``I can see very long distances.  Put the gun down, Miss Militia.  The cat's out of the bag.''



``You're \emph{admitting} it,'' Chevalier said.



There was another rumble, shaking the ground so hard that most of us lost our balance.  Legend stayed perfectly upright, no doubt using his flight to hold himself a hair above the ground.  He turned to check the fighting hadn't started.



``It's true?'' Gully asked.



``We started Cauldron in the early days,'' he said.  ``They had a way to give people powers, and each of us were desperate for our own reasons.  We \emph{should} have had trigger events, but we weren't lucky enough to have the potential.  Nobody deluded themselves about the risks.  We knew that it was all too possible to die or become a monster.''



``But you did.  You made monsters,'' Gully said.



``Everyone who took a dose went into it with their eyes open,'' he said.  ``They refined the process, and we reduced the chance to a single digit of a percent.  Two, three percent, if that.  And at the same time the numbers were decreasing, we were realizing how badly we needed the heroes that Cauldron could provide.  Capes without traumas to drive them toward villainy.  Cauldron turned it into a business, producing heroes and acquiring funds from the wealthy to redirect to Endbringer recovery and further research into powers.  We knew it wasn't ideal, that some would turn to villainy, but with the appearance of the Slaughterhouse Nine and the damage the Endbringers were doing, we had to do \emph{something}.''



``How do the Travelers factor in?'' Miss Militia asked.



``They got ahold of a dose meant for another group of people.  They weren't screened, they didn't follow the necessary procedures, didn't get the psychological or physical checkups\ldots and even with that, we had no idea that the formulae could produce anything like this Echidna.''



``But the Travelers are from another world,'' I said.  ``Aren't they?''



``The Simurgh,'' he said, simply.  ``Madison, Wisconsin, one and a half years ago.  She opened a dimensional gate.  You were there, Myrddin.  You met Trickster and Echidna.''



Myrddin's eyes widened.  ``The hospital room.''



The ground rumbled again.  A burned husk of a building at the far end of the street toppled with a crash.



``But\ldots if Cauldron's not taking people from other worlds,'' Gully said.  ``What--''



``It's not Cauldron,'' Legend said.  His voice was flat, without affect.  He met her eyes.  ``Manton worked for Cauldron, before an incident with his daughter led to a psychotic break and a break with the organization.  He left with samples that he passed on to others.  One of those people sold them for personal profit before Cauldron found him.  Another was responsible for the case fifty-threes.  We thought it was Manton, but it wasn't.''



He glanced at Tattletale, and she cocked her head a little to one side.



``\emph{Why}?'' Gully asked.  ``Why do that?  Why make us like this?''



``I'd give you answers if I could.  Some people abuse others for the sense of power it gives them,'' Legend told her.  His voice sounded hollow.  ``To change someone's body and mind completely and irrevocably?  It could be the same impulse.  The appearance of the case fifty-threes has stopped or slowed dramatically.  It's little consolation, but we think the person who did this to you is be dead or completely out of formula.''



``That's no consolation at all,'' Gully replied.  The ground shuddered.



``It's worth noting,'' Legend said, ``That we tracked Manton down.  He and Siberian's master are the same person.  Dragon and Defiant have a bead on the Nine.  They expect a confrontation to start soon.''



But I could only think of when Legend and I had been looking down at the Nine from above.  He'd recognized the Siberian's master then, and he hadn't told me.



Was he omitting facts \emph{now}, in the same way?  Was he lying like he had then?



``The Siberian is Manton?'' Myrddin asked.



Legend nodded.  ``And Manton is ultimately responsible for the case fifty-threes.  I know it's not the explanation you each hoped for, but it's the reality.  Understood?''



There were nods all around.  I wasn't sure if anyone else saw, or if they knew her well enough to say, but Tattletale was smiling, and it wasn't the one she wore when she was being friendly and easygoing.  It was the one she'd had before she'd unloaded on Panacea, back at the bank.  The one she'd had before she revealed to Coil just how she'd screwed him over.



I directed a bug to fly across her face, brushing the skin.  She flinched and looked at me.



I only stared at her, \emph{willed} her to be quiet.  Saying anything would be disastrous here.  I wasn't sure how much of what he was saying was truth, but Legend had just stepped in here, pacified the situation.



Tattletale shrugged with one shoulder, a fractional movement that only my swarm really noticed.  The smile disappeared from her face.



``Sure,'' she said, a little belatedly.



The rumbling continued, steadier now.



``Is that the essence of what you wanted to tell us?'' Myrddin asked me.  ``What Legend said about Cauldron?''



``Only thing I'd have to add is that the Travelers came from another Earth.  Except for Trickster, they're more or less on our side here.  Tell Ballistic, Sundancer and Genesis that we can get them home, and they'll help.  They have the kind of firepower we need.''



``We'll--''



My bugs sensed Echidna clawing her way to the surface.



``Armband!''  I interrupted Chevalier.



``What?''



``Warn them.  She's here!''



It was too late.  The Grue that was accompanying Echidna emerged from the hole she'd dug.  He raised his hands, and I could see the wave of darkness rolling out from the entrance to a parking garage to sweep over the assembled heroes.



She wasn't beneath the fallen base.  With her shapeshifting and the teleporting Grue's help, she'd found her way through a side tunnel, clawed or punched her way up into a nearby parking garage, a place where she could stage her attack.



Echidna materialized out of the darkness the Grue had created.  She was nearly twice the height she'd been before, to the point that the human body on the top was miniscule, a speck by comparison.  A human figure atop a broad three-story building.



Her legs were more robust, now.  There weren't any feeble limbs like the ones my bugs had glimpsed or touched.  Her lower body was plated in a crust of bone, and two more heads were just emerging from her front, one with the beginnings of a mouth, the other with two large eyes and a lump that would become a snout.  She'd developed.



There were no less than ten capes within range of her claws as she appeared.  Ten capes that were caught in her flesh the very instant the fighting began.



I'd placed bugs on Legend to track his movements, and they went with him as he took to the air and fell into formation with Alexandria and Eidolon.  Those same bugs allowed me to sense the smallest movement of his head, as he directed a slight nod toward his longtime comrades.



If I'd been suspecting that he'd been lying before, that clinched it for me.



In his shoes, I wasn't sure I wouldn't have done the same.





