





The Grue Echidna had created turned his attention to the rest of us.  His power massed around him and then flowed forth like a tidal wave of crude oil.  I was already atop Atlas, rising into the air.  I couldn't avoid the fact that Scapegoat was in the truck, and if we were separated-



I flew after the wave of darkness, tracing its path as it met Scapegoat's van and making my best guess at where it would wind up.



The darkness hit a wall, and the van materialized, solid once more.  More heroes were deposited two or three city blocks away from where they'd been standing.



My heart was pounding in my chest as I blinked a few times and double checked that I hadn't gone blind.  If the Grue had cut off Scapegoat's power, or if he'd delivered enough of an impact to disrupt it, it could have left me in worse shape than before.



I could see, and I could breathe.  Scapegoat was safe inside the containment van.



He'd scattered us.  Our tight battle lines were now spread out over city blocks, and people were having a surprising amount of trouble getting their bearings.  One of the team leaders managed to get his squad organized, pointing them in the right direction, before Echnidna's Grue hit them again.



There was a limit to what I could do.



I gathered my bugs and started working out how to stop the Grue.



I had cords pre-prepared.  I spliced a number together into a hundred-foot long line, then had my bugs fly the cord out.



A minute later, my fastest flying bugs were winding the cord around the Grue's neck, while others were biting and stinging.  He barely even noticed, beyond swatting at the insects wherever they landed.



I needed something to tie him to.  A telephone pole?  It wouldn't stop him or even hamper him in what he was doing to disrupt our fighting lines.  If he could teleport himself, then it wouldn't even hamper him at all in the long-term.



Legend, Eidolon and Alexandria moved into the fray, accompanied by a number of other flying heroes.  They were coordinated enough that they had to have planned it out in advance.  Alexandria went in first, circling around and then swooping down to strike Echidna across one back leg.  She stuck on contact.  Through a combination of her own strength and one of Legend's lasers, she got free before Echidna could turn and envelop her.



Eidolon was making his move before Alexandria was even free.  He cast out a bubble that swelled as it moved through the air.  By the time it reached Echidna, it was twice as big around as she was, enough to reach from one sidewalk to the other.  The colors around her became muted, and her movements slowed to a tenth of the speed.



It was a time-distortion effect.  Legend took the opportunity to emit twenty individual laser beams.  They each flowed out as a steady, unfaltering stream, and turned in mid-air to punch into Echidna.  Each was meticulously placed to drive through the center of her body and avoid the places where her victims were being absorbed, or even cut her victims free.



One beam turned down and took a sharp right to strike the ground just to the teleporter-Grue's right.  It slashed towards him and he used his darkness to teleport himself to safety, cutting the cord I'd created in the process.



I commanded my bugs to collect the thread and cart it to the destination he'd teleported to.  It was futile to try to tether a teleporter, I knew, but if I could find a way to trip up his abilities, tie his ankles together at a crucial moment\ldots \emph{something}, it might help.  Beyond that, I'd have to hope the venom brought him down.



Echidna tried to move to one side, but Legend's beams followed unerringly, swelling in size and number.  Thirty, forty, fifty\ldots each cutting their way through her flesh as though she were made of little more than snow.  Smoke or steam billowed around her as her flesh charred and boiled.  The lasers might have been affected by the time distortion, but that didn't matter when the lasers were moving at the speed of light in the first place.



She feinted right, then lunged left, but Legend's aim didn't err in the slightest, and Eidolon's slowing effect drifted after her.  Still, Echidna moved faster than Eidolon's slowing effect did.  Slowly but surely, as pieces of her flesh were carved away and left to fall to the ground, she made progress toward the effect's perimeter.



Alexandria flew low to the ground, striking and catching hold of a traffic light.  In one second she was a blur, the next she appeared to be moving as fast as a person did when they ran.  Charging into the effect's area, Alexandria made a beeline for Echidna.



The swing was slow motion, but Echidna was too.  Alexandria struck her with the metal pole, and Echidna moved like she'd been hit full strength.  Her front claws were lifted off of the ground by the force of the blow, and she reared up, the canine faces contorting in pain and anger.



The lasers moved around Alexandria, passing within centimeters of her.  She didn't even flinch as she lowered herself to the ground behind Echidna, used her hands and one knee to correct a bend in the pole, and then stabbed it into one spot on the back of Echidna's leg where a hero was trying to get free.  Legend's cutting lasers and the leverage of the pole pried him free.  Alexandria caught him before he hit the ground and threw him.



Other heroes saw and positioned themselves before he reached the edge of the effect.  He resumed normal speed and the heroes caught him.



Echidna's Grue blanketed the area in darkness, and Legend opened fire on the area where the darkness had originated from; the ground floor of a nearby grocery store.  My bugs identified the Grue on the far side, and with a moment to get arranged, they connected the ends of cords.  A little shorter than a hundred feet, now.  If I tied it to a section of a nearby window, and he tried to run, it could maybe yank him off his feet, but that didn't amount to much.



The Grue teleported Echidna to him, freeing her from Legend's attack and the slow effect.  The darkness carpeted them and bought her a second to breathe and regenerate.



Had to remove the Grue from consideration.  I tried to visualize what would happen next, anticipate their next move.  Noelle would throw herself into the fray again.  Either he'd use his teleportation to do it or\ldots



I tied the other end of the cord to a piece of bone plate that stood out on Echidna's side.



Eidolon was pointing to the building that Echidna had materialized behind, pointed two fingers at it with a thumb extended in a gesture much like a gun.  Legend took the signal and opened fire, unleashing countless lasers into the ground floor of the building.



The Psycho-Grue took shelter, ducking to one side of a nearby dumpster.  At the same time, Echidna did just what I'd hoped for: she bolted.  The cord went taut, and the Grue was pulled off his feet by the suddenness and force of her movement.



I hadn't tied it into a proper noose, but the cord \emph{was} around his neck.  I'd read somewhere that nooses tended to kill because they broke the neck rather than by suffocation, provided they were tied right and there was enough of a drop.



This wasn't a drop, but it \emph{was} a tough cord around his neck, and the creature on the other end weighed no less than fifteen tons, maybe twice that.  She'd accelerated from zero to fifty in an instant, and he went limp almost immediately, dead or completely disabled in a heartbeat.  My bugs cut the cord and held it ready.



Echidna hadn't used her power yet.  She'd absorbed enough capes, but something was holding her back.  I wondered if her regeneration drew on the same pool of flesh-generation that made the clones and she couldn't make clones while healing the kind of heavy damage the Triumvirate was dishing out.  Maybe there was some other drawback.



The `shoulders' of her lower body scraped and dragged against the sides of buildings as she stampeded through the back alleyways.  She kicked a dumpster and sent it careening as she ran, brushed against a fire escape with enough speed and force that it was ripped from the brick wall.



She was very nearly out of my power's reach when Myrddin cut her off.  He waved his staff and a group of heroes materialized around him.  Tecton and Chevalier were among them.



The heroes around me were trying to get sorted into squads again.  I was aware of someone driving the van that held Scapegoat.  Taking him in the wrong direction.



I drew arrows with my bugs on the dashboard and prayed that whoever the cape was behind the wheel, they were aiming in the right direction.



Seeing how the heroes were struggling to get organized, suffering for the lack of armbands to help them navigate and get essential information, I decided in an instant that I needed to guide more than just the van.



I began drawing out arrows and letters.



I drew out an `E' with an arrow pointing in Echidna's direction, a hundred times in a hundred places.  Above Echidna, I set swarms of insects to flying in formation, tight circles and figure-eight loops, vertical or horizontal.  Letters and words formed.  Echidna, Myrddin, Chevalier.  Did the `e' go after the `i'?  Couldn't remember.  Was supposed to be `i before e, except after c', but there were more exceptions to the rule than there were correct uses.



Shaking my head to stir myself awake, I tried to refocus, paying attention to the primary site of the fighting.



Echidna charged Myrddin and the heroes that accompanied him.  He used his staff to draw something into the air.  My bugs could feel a vibration, see the white blur of a light source.



The sign he'd drawn exploded outward, striking Echidna on her right side.  It was enough to alter her course, and her shoulder slammed into the corner of one building.  Her body dragged against the building's face until that she had to stop and pull away.



Chevalier pointed his sword at her, fifteen feet long, and pulled a trigger.  A blast erupted down the center of the sword's mass, and a cannonball caught one of Echidna's monstrous heads between the eyes.  Through the composite vision of all my bugs, I could get a sense of the damage that had been done, the spray of gore.



I was too tired to be focusing on my bugs to this degree.  My awareness of my real self was faltering.  I was unconsciously updating the positions of the arrows to allow the heroes to home in on Echidna, but I also had to work to keep myself close to Scapegoat, and I wanted to make sure I knew where Bitch and the others were.  Atlas was following my unconscious commands, but that meant I was straying a dangerous distance from Scapegoat.  Had to be safe.



The arrows I'd drawn for each of the heroes \emph{were} working, though.  Heroes were moving towards Echidna with purpose, now, and the van with Scapegoat inside was moving in the right direction.  I caught some squad captains giving orders.  A cape that could speak over distances was relaying information to Myrddin and Chevalier.



Tattletale was on the ground, but she didn't advance toward the scene of the fighting.  She had gotten her hands on a cellphone, and was speaking steadily into it, relaying information. I only caught some of it – I couldn't devote that much focus to her.  It was about Noelle.



Chevalier and Myrddin made an effective duo.  Chevalier's power had made his armor virtually impervious, his cannonblade massive, each effectively many times as dense and/or many times as large as they should be, but he was still able to treat them as though they were the normal size.  He swung his sword as though it were barely there, and when he found an opportunity to strike out with a gauntleted fist, the effect was always far greater than the hit deserved.



Not so different from Fenja and Menja, only his gear was the focus, not himself, and he was a little more versatile.



Myrddin, for his part, coupled versatility with raw power to devastating effect.  He had a bag of tricks and switched from one to another without hesitation.  Echidna spewed a stream of bodies and gore, and Myrddin drew a dark sign into the air, suctioning the incoming matter into it.  I sensed Chevalier and Tecton slamming their weapons into the nearest surfaces to avoid being pulled in, catching hold of allies who weren't so capable.  Then my own bugs were yanked toward the crevice and violently crushed against all of the other debris, leaving me momentarily blind in that area.  More of my bugs flowed in, giving me time to see Chevalier delivering a series of powerful sword strikes and cannon shots at Echidna, not letting up.  He paused, throwing himself into a side-alley as Noelle tried to stomp on him, and Myrddin released the matter he'd suctioned in as a condensed bullet of gore, dust, crushed bodies and dead bugs.



Perhaps the strongest thing about the partnership between the two heroes was how well it accommodated others.  Heroes with ranged powers were free to unload on Echidna while the other two fought, and heroes like Tecton could offer further support, destroying the ground beneath her feet.  She was big enough now that he couldn't trap her, but he could make her stumble, or bring concrete from the nearby buildings raining down on top of her.



The Triumvirate flew straight over Echidna, and Legend opened with a laser beam I could see from three blocks away.  He killed some of the bugs I'd been using to draw words in the air in the process.  That was as much my fault as his.



Echidna was more or less trapped, forced to back away, but unable to fully turn around with the walls of the alley on either side of her.  Eidolon threw down another slowing bubble behind her, and Alexandria dropped to ground level to stand behind Echidna and stab the metal pole of the street light through the knee of one of Echidna's back legs.



There was nothing for me to do beyond helping to organize the others.  I made sure to draw arrows and words high enough above the buildings that anyone approaching the scene would be able to tell that Alexandria and Chevalier had Echidna flanked.



Atlas carried me above the scene, a distance away from the Triumvirate, but still close enough to see into the alley.



Echidna was sustaining a beating, and there were only four directions she could go.  She could go \emph{up}, which was the only route available to her that didn't involve going through a solid surface, but that involved running face first into the laserbeam that Legend was firing straight down from above.  Going \emph{down} involved tearing through pavement and whatever was below the road.  Even if there was a storm drain or some other underground space to enter, she was doubtlessly sustaining too much damage to take the time to get that far, and she was too big to fit, unless the area was cavernous.



That meant she was bound to head either left or right, through walls of brick or concrete.  I was careful in how I positioned my swarm, putting them on walls so I could tell if she knocked one down on her way through, while keeping the bugs out of her likely path.  Cloned bugs were the least of our problems, but I wasn't about to contribute to her arsenal.



I'd drawn heroes closer to the scene of the fight with my directions.  Now I had to communicate the danger.



I spoke through my bugs, moving each closer to the capes.  The swarm was spread out, which made the resulting voice thin and reedy to the point that I wasn't sure if it was audible over the noise of the fighting in the alleyways.



``\emph{Incoming},'' my swarm buzzed.



More than a few heroes jumped at that.



``\emph{Look for my signal},'' I said, ``\emph{She'll have to go through the walls to escape.''}



Many of the squads were in or around the alleys but not actually participating in the fights.  With arrows and the movement of my swarm, I did my best to indicate the ways to the walls she might head for, and I drew exclamation marks on the faces of the buildings next to her.



It didn't take her long to reach the limit of her patience.  She tried to advance on Chevalier, only to get driven back by Tecton, Myrddin and one or two ranged capes.  Backing up meant running into Alexandria, who was stabbing and swatting with the pole that had held the traffic light.



One claw ripped through brick and wood, and she plunged into the building to her left.  She was tall enough that she had to hunker down, and she was \emph{still} shoving her way through the flooring that separated the first and second floors.  Her route put her on a path for where the fighting had originated, where the majority of the heroes were now waiting.



She could wade through brick and concrete and leave a building folding in on itself in her wake, but dealing with a mass of capes proved more difficult.  Forcefields blocked her movements, and a half-dozen heavy hitting capes like Grace were waiting to blindside her.



A heartbeat after the first wave assault passed by, Chronicler's replicas of the melee assault group tore through Echidna a second time.



Echidna fell over, and was in a position to see Legend, Alexandria and Eidolon overhead.



Some capes had stayed in the fray, including types like Weld and Wanton, who couldn't be absorbed and couldn't be affected by the capes with ranged attacks.  They joined in with the Triumvirate's attacks on the fallen foe.



She vomited, but it wasn't the same as before.  Her vomit this time was thick with bodies, to the point that it didn't \emph{spray}.  The vomit tumbled from her four mouths as a sludge that met or exceeded her total body weight in sheer volume.  Worse, where it had maybe been ninety percent liquid and ten percent people, before, the numbers had inverted.



Legend raked a laser across the piling, writhing, reaching bodies, but Echidna was getting to her feet, throwing herself into the building behind her.  She'd done enough damage with the last maneuver, and her return trip brought a wall crashing down.  Powers of all kinds were brought to bear as the capes on the ground did what they could to save themselves and their teammates.



I could have stayed, helped with the wounded, but the van with Scapegoat was moving on, and I was worried about what might happen if Echidna managed to get away.  She was wounded, but regenerating, and bodies kept pouring forth from her mouth.  It would be best to leave the wounded and dying to the less mobile capes.  I was more useful in the fray, though that didn't say much.



She was moving at a good pace.  Only the fastest were able to match her in speed, and few of those were \emph{also} capable of slowing her down so the rest of us could catch up.



A trail of clones flowed in her wake.  All of them were capes, and even though they were unclothed and unarmored, some were taking more than a few hits to finish off.  Worse, at least one of the people she'd caught was a cape in much the same vein as Prism had been.  A self duplicator.  It amounted to scores of bodies, where one in twenty were capable of copying themselves, and maybe three or four in twenty were tough or borderline invulnerable.



I joined in with the other heroes who were fighting to kill or mop up the clones before the psychotic things could get organized.  They were lumped together as a tangle of limbs, heads and torsos, and each was tacky with the fluids of the vomit.  My swarm made contact, and began ruthlessly doing as much damage as I was capable of.



Myrddin caught up and hit her with one of his `spells'.  Echidna promptly disappeared in a clap of thunder, and Myrddin went very still, floating in the air.



From his controlled breathing and lack of celebration, I could only assume that Myrddin was concentrating.  Echidna wasn't dead and gone, only held at bay for the time being.  I was willing to bet it was the same effect he'd used to carry Chevalier, Tecton and his other teammates into the fight in the alleyway.



In the meantime, the rest of us were left to dispatch the clones as quickly as possible.  They were frailer looking, with features missing.  There were clones without ears, clones without noses, clones with missing fingers.  Half finished, their skin was so thin as to be translucent, and most lacked hair or their hair was so sparse as to barely matter.  The skin of most broke and bled where my bugs bit, as though it were little more than wet paper.



If my swarm was made up of countless tiny surgeons, doing strategic damage, Rachel's dogs were the opposite.  Bentley plowed through the ranks of the clones like a living bulldozer.  He wasn't running full-bore, but he wasn't slowing down at any point either.  The other dogs followed, each roughly the size of a pony, chained to Bentley's harness.  The dogs fought among themselves in their struggles to attack and wound the clones, but I could see Rachel doing what she could to ensure that none of them were \emph{killing}.



She'd done the same with Bastard.  It made sense, in a way, that she didn't want them to get accustomed to killing before they were fully trained.



The clones weren't wholly helpless, though, fragile as they might be.  They \emph{did} have powers.  Through the bugs of my swarm that lingered on the combatants, I could track the fallen.  Two heroes down, injured or dying, another deceased.



We were outnumbered, and we couldn't \emph{afford} to lose one person for every twenty clones that fell.  Echidna had created at least a hundred clones in the course of her last getaway.  She would create a hundred more when she reappeared, if we didn't find a solution.



Legend found a position to open fire from, and sent a barrage of lasers down toward the trail of bodies, while Alexandria followed the direct path that Echidna had taken, darting left and right to strike out and kill even the tougher capes in a single hit.



In the midst of the chaos, a speaker began blaring at the top of one containment van.  The same voice that had come from the armbands.



``\emph{The following information has been disseminated, and remains unconfirmed.  Echidna is in a rage state.  The monster is in control, not the girl.  Seventeen capes are currently within her.  Her rate of regeneration and production of clones is derived from a central core within her lower body that produces an endless quantity of biological material.  A body part severed from the core will die.  Destroying the core in entirety will destroy her\ldots''}



\emph{Tattletale}, I thought.  She'd passed on the info she'd gleaned.



Scapegoat was out of the van and shouting.  Weld was among the capes that came to his assistance.  He held a female clone in his iron grip, with one hand over her mouth.



Tecton and Wanton moved to help, and Scapegoat looked up at me, gesturing.



Pointing at the ground.



\emph{Would have been easier if he'd just said it}.  I found a clear spot on a rooftop and landed.



The second I was settled, Scapegoat laid his hands on the clone Weld had caught.



As before, the sensations hit me.  Phantom sensations of every possible texture and experience rippling across my entire body.



This was why he'd told me to land.  He'd been worried I might lose control of my power, maybe losing control over Atlas and fall.



I just had to endure.  I could control my bugs to some extent, though flight wasn't so possible.  One of the clones had broken away from the fighting, and my bugs were both attacking her and pointing the pursuing capes in the right directions.  She split off into four copies.  The heroes killed three of the four, only for the survivor to split off into a quartet once again.



If I'd been thinking about containment, I might have set triplines at each of the major intersections, cutting them if and when heroes passed through.  As it was, I couldn't stop her retreat, and could only try to blind her, choke her and distract while they closed the distance with my direction.



But she was fragile, like most of her fellow clones.  Mandibles tore her paper-thin skin, and more bugs found her jugular.



Just like that, she died with blood spouting from her throat.  She created duplicates of herself, but they were created with the same injury.



The capes caught up to her.  One murmured, ``Kudzu.''



``\ldots{}s not her, Jouster,'' another said.



Elsewhere, Regent was dispatching other clones.  He deftly tripped up the more mobile ones and closed the distance, then executed them with a quick stab of a knife.



The sensations kept hitting me.  It was a deeper sensation now.  Tastes, vision, hearing\ldots everything under the sun, fragments of a million different sensations.  Picking through the noise was nearly impossible.  I had to find refuge in my swarm's senses, disassociate from my body\ldots



If I hadn't been trying so hard, I might have missed it.  It was more subtle than the first time I'd heard it.  A keening noise that my own ears couldn't hear.  Even many of the insects were unaware.



Using my swarm, every bug in the four block range, I buzzed out the alert.



``\emph{Shatterbird!}''



Some capes reacted fast enough.  Helmets with visors were torn free, intact armbands and cell phones discarded.  Some erected forcefield barriers.  I was tearing off my mask, bundling it in the fabric that hung around my legs.



There were others too caught up in the fighting, yet others dependent on hardware with silicon chips that they couldn't shirk so quickly.



It wasn't as strong as her last big attack; there was less glass in the city to carry the effects.  Still, I could hear the resounding crash of everything glass in this half of the city breaking.  A tidal wave of destruction rolled past us, leaving countless injured in its wake.  The attack was weaker, but not necessarily \emph{weak}.



Tecton had been left immobile, components of his suit destroyed.  The clone and Scapegoat were down, struck by the glass from the van's windshield.  Chevalier had been caught by something, a fragment of glass that had penetrated a slit in his visor, and he was struggling to fight three clones and avoid hitting his teammates, all while partially blind.



I checked myself.  I could breathe, I wasn't blind.  All despite Scapegoat's disabled state.



Had he transferred the conditions to the clone?  Was I in the clear?



I wasn't sure, and I wasn't sure I could afford to take the risk and stray beyond that one-hundred and fifty foot range of his.



The direction the attack had come from\ldots  Shatterbird had stayed behind, used her power from the base.  I'd assumed it was because Echidna had eaten her, but it was all too possible that they'd found another route.  Inducing temporary unconsciousness?  Or perhaps Echidna had eaten her and then spat her out right away, to induce enough weakness that Regent couldn't use her.  I'd have to ask Regent for details, and that wasn't an option.



No, there were bigger worries.  Battle lines had broken, and simply by virtue of being more numerous than we were, many clones were still standing.  It made only a small difference, but it was still an advantage for their side: the clones weren't wearing or carrying anything glass.  An advantage of being naked.



The big heroes were trying to get organized.  Myrddin was still keeping Echidna out of the fight, the Triumvirate were exchanging quick words as they tried to figure out whether they should stay for when Echidna popped back into existence or help with the clones.  Legend shot as he talked, and Eidolon was casting out blue sparks that flew forth.



Clones were advancing on Scapegoat and Tecton.  Weld was there, but he wasn't quite enough.



I stood on Atlas' back as he descended to the road, shaking my mask to let the glass fall free before carefully pulling it back on.  Weld glanced at me and nodded as I appeared at his left, helping to form a defensive line.



Weld's hands started to change into long blades, and with the reach they afforded him, he was able to defend more ground.



I stepped off Atlas and let him stand on his own, his scythelike forelimbs raised.  He wouldn't be \emph{that} good in a fight, but the clones were fragile, and two more weapons was better than nothing.  My knife and baton slid free of their respective slots in my compartment, and I whipped the baton out to its full length.  It offered me a little more reach, an excuse to take one more step away from Scapegoat's body and the frozen Tecton.  In this fashion, Weld, Atlas and I formed something of a triangle.



Being on the ground, it added a kind of reality to the situation.  On a technical level, I was more \emph{aware} of the bodies when I used my powers, more aware of the enemy numbers.  Here, though, I could see only the crowd.  Hero and clone were fighting, the ground was littered with the dying, the maimed and the dead.  There were countless people who needed help, people who I couldn't personally reach.



My \emph{bugs}\emph{ }could reach them.  I did what I could, trying to blind the right people, to injure and maim clones where I could ferret out vulnerabilities.  Most of the vulnerable clones were already out of the fight, leaving us with only the more troublesome ones.  The duplicators, the durable and the mobile.



I was fighting a duplicator.  Another Kudzu, like the one I'd killed earlier, unless there was another Asian duplicator with a Japanese-sounding name.  She was vulnerable, but she knew how to fight.  Better than I did.  My advantage was my weapons and my armor.  Hers was her relentlessness.



My baton crushed one skull like an overripe pumpkin, my knife caught another in the chest, pushing past bone like it was a willowy tree branch rather than anything more solid.  I kicked her in the chest to help pull my knife free, and suffered a painful kick to the side of my knee before I was able to retaliate.  I fell, tried to strike the offending Kudzu with my knife, but she caught my wrist.  A swing of my baton was caught as well.  I got my feet under her and thrust my head into hers as I returned to a standing position  Her face was softer than my mask was.



She fell, and the fourth Kudzu formed three new doubles before I could advance and attack her.  One kicked me hard enough that I had to lean against Tecton's armor to get my balance.  My swarm had hurt the one Kudzu who'd stayed back, and the new doubles were feeling the same pain, but they were still fresh, weren't tired or hurt from previous rounds.



Weld fought with an invincible man who was smoking, his hands hot enough that they were heating Weld's flesh.  The man grappled him, and Weld's attempts to strike him were having little effect.  The man dug his fingers into Weld's chest, and white-hot metal dripped to the ground.  He was digging for organs.



I hated to spare bugs when I was fighting the Kudzu-clones, but I sent some Weld's way.  They coated the man, and found some flesh they could damage.



``His back, Weld!'' I shouted.  ``His front half is tough, but everything that isn't facing you is vulnerable!''



A Kudzu took advantage of my distraction to club me.  I retaliated by stabbing her, a nonfatal blow.



Weld pulled one arm free, reached behind the man, and started sawing into the back of his head.  Serrated edges formed on the blade, to allow for a better cut, Weld found something vital, and the man slumped to the ground.



He turned to help me with the Kudzu.



A scattering of Legend's laser bolts tore through our surroundings, though he was blocks away.  Three of the Kudzu I was fighting were hit by Legend's shots, and Weld lunged forward to stab the fourth.  The least hurt of them vibrated and split off into a fresh set of quadruplets.



\emph{Clones of clones}, I thought.  I could only swear in my head.  My lungs weren't suffering like they had been earlier, but I was short on breath nonetheless.



Overall, our side was winning, but we weren't winning \emph{fast}.  Nearly a third of us had fallen when Shatterbird hit, and more were losing in this chaos that followed.



Which made this the moment, fittingly, when Echidna popped back into existence.



Eidolon and Legend had been doing what they could from range, and now they were forced to deal with Echidna, leaving the rest of us to deal with the remaining clones.



Legend started using a massive laser to tear into the piles of clones that spilled forth from her mouths.



One Kudzu-clone shouted.  ``Cover me!  I got this!''



Roughly a quarter of the remaining clones broke away from their individual engagements, including the Kudzu I was fighting.



\emph{Fuck me, they're cooperating}.



Our side did what they could to stop them, but these clones were still in the fight because they were hard to kill.  My bugs attacked the Kudzu, and I gave chase to stab one, then another in the back, before my hurt knee gave out and I fell to a kneeling position.  Bitch and her dogs threw themselves into the ranks of the clones, tearing and rending, but it wasn't \emph{enough}.



Chevalier wasn't far from me.  His cannonblade detonated, painfully loud in my ear, and four or five clones died with each shot.  Legend's lasers tore into their ranks, and Eidolon threw down a slowing field to stall for time.



It was too little, too late.  They were making a beeline for Echidna, for Legend, Alexandria, Eidolon and Myrddin.



The Kudzu who'd shouted got close to Echidna, and a tongue circled her throat.  She was reeled in, and stopped herself at Echidna's mouth, bracing herself in position.



Chevalier took aim and shot.  A miss.



Miss Militia's rifle shot was on target, punching through the front of the Kudzu's throat.



But the Kudzu's death wasn't instantaneous, and she had time for one last gesture.  Echidna vibrated, and then split off into four copies.



\emph{Four copies of Noelle}.



My breath caught in my throat in the moment I processed the reality of what had just happened.  I managed to huff out a small shuddering breath.



They were withering and dying like Kudzu's obsolete clones were, slowly but surely, right off the bat, but there were still \emph{four} of them.



This was Echidna's greatest weapon.  Ballistic had talked about her sense for tactics, but that was Noelle, really.  This was \emph{Echidna}, and she was too gone for much of that.



No, the variations that naturally occurred in powers laid out a range of capes.  Virtually every power was offensive, just about every power had \emph{some} use.  That was the norm, the standard.



But exceptions existed.  They were the Bonesaws, the Crawlers, the Echidnas, the Legends, Alexandrias, Eidolons and Dragons of the world.  By sheer fortune, they'd stumbled onto powers that set them head and shoulders above everyone else.  Having the right variant, being in the right situation to use that power.



If one in a hundred capes met that kind of standard where they were just that much more versatile or powerful, then Echidna could make a hundred capes, and chances were good that one of those would be exceptional in that way.



An Echidna-double turned and charged straight for us, stampeding through the clones to get to the troops on the ground.  Forcefields went up, Chevalier unloaded cannon blasts to stall her advance, and we all did our best to retreat.  I took to the air with Atlas.



The other two Echidnas, including the original, started fighting the big name heroes.  Tongues lashed out, and Legend severed them with cutting lasers.  The clones vomited geysers, spitting out no clones with the fluid, and Alexandria bore the brunt of the blow.



Eidolon was creating blue sparks that floated around him, but when Alexandria began to lose in her struggles to keep the vomit from reaching her comrades, he switched to using a slowing field instead.  He cast it down around two of the Echidnas.  The one he didn't catch vomited, and he threw up a small forcefield to ward off the attack.



A narrow tongue was hidden in the midst of the vomit, a concealed attack.  Prehensile, it snaked out and caught him by one arm.



Eidolon was pulled in, and clipped the forcefield he'd raised with enough force that he was momentarily stunned.  The forcefield and slowing fields disappeared, and Alexandria was caught off guard by the sudden increase in her opponent's speed.  



Caught against its back, she started to tear herself free with the help of one of Legend's cutting lasers.  A spray of vomit forced Legend to abandon his efforts to save his teammates and retreat for his own safety.  He cleaned up the clones that the original Echidna was still producing.



A second later, one of the Echidna-doubles leaped on top of the other, sandwiching Alexandria between her and the other Echidna-double.



The \emph{real} Echidna closed her mouths, and the vomiting stopped.  She stepped on the tongue that had a hold on Eidolon, then stepped on the caught Eidolon.



Legend did what he could, but even with the three Echidna-doubles looking more like the walking dead than anything else, he couldn't do enough lasting damage to any of the brutes.  Miss Militia and Chevalier contributed some ranged fire, as did the heroes on my side of the battlefield, but the Echidna-doubles used their bodies to block the worst of the incoming fire.



Echidna bit deep into her double, tore at flesh until she found the morsel caught between their bodies.  Alexandria.  I could see the muscles in her throat working as she swallowed.



Each of her doubles made a final reckless charge before falling to pieces.



A hush of sorts descended on everyone present.



Two of our best, caught.



Echidna reared back a little, then spat, as though she were coughing out a morsel of food she'd been choking on.



An Alexandria.  Had to be, with that long black hair.  The woman stood, and I could see how she was missing an eye.  She brushed her hair to one side, so it covered half her face, and I could hear a murmur.



``Director Costa-Brown,'' someone in the crowd murmured.



The Head of the PRT and Alexandria were one and the same.



I couldn't bring myself to care.  I wasn't sure if it was just that I was in shock, that I was more focused on the fight that was looking a hell of a lot less winnable, or a simple lack of surprise that the PRT would have been so corrupt and imbalanced as to have a major balancing factor missing from their ranks.



Miss Militia took aim with her rifle and shot.  The bullet sparked as it clipped Alexandria's forehead.



Alexandria shook her head.



Another cough, another spit.



Eidolon.  I couldn't tell if he was unattractive by nature or if it was just mild deformations.  He looked so \emph{small}, so below \emph{average.}



He found his feet.  Miss Militia shot him twice, and he fell back against Echidna's leg.



He flickered, and the wound was smaller, another flicker, and the wound almost disappeared.  Each flicker was stronger than the last in how it reversed the damage.  He staggered to his feet again.



``Go!'' Chevalier screamed, breaking the frozen silence.  ``Before he's at full strength!''



We charged.  There was no other choice.  If we didn't win \emph{now}, \emph{everyone} lost.





