





The Eidolon-clone apparently wasn't worried about the mass of armed heroes that were mobilized against him.  No, his concern was being naked.



He touched Alexandria, and she flickered.  When the flickering died out, she was dressed in a costume; a long white cape, a white bodysuit with high boots and elbow length gloves and a stylized helmet that let her long black hair flow free.  The tower on her chest was a tumbled ruin.  The ruined lighthouse.  A mockery of her other self, the colors reversed.



I \emph{really} wasn't liking the implications for that flickering power.  Healing, the costume\ldots



Legend shot the Eidolon-clone before he could do anything more.  A laser tore into the Eidolon's chest cavity, slashed out to carve into Echidna's foremost leg, causing it to buckle mid-step.



The Alexandria-clone floated up, interjecting herself between Legend and his targets.  He adjusted the beam's orientation, and she moved to block it.  He divided it in two shots that she couldn't block, and she charged him.  Legend broke off to flee.



I could see the Eidolon flickering to heal himself as Echidna charged the rest of us.



Our battle lines did what they could to slow her down, which didn't amount to much.  She was massive, now, to the point that cars were trampled beneath her or sent rolling on impact.



Chevalier put himself directly in harm's way.  He held his cannonblade out to one side, and I could see it swelling in size.



There were a hundred feet between them, seventy-five, fifty-



The sword was growing with every moment, as well.



He brought the blade down to the ground, a razor's edge biting deep into pavement, the blade's point directed at Echidna.  Then he pulled the trigger.  The fact that it was impaled in the ground kept the recoil manageable, and the fact that it was as large as it was meant that the effect was that much more impressive.



Echidna leaped to the side as the cannonball ripped out of the weapon.  Not quite fast enough, she wasn't able to avoid the worst of it.  Three of her eight legs, all on one side of her body, were turned into flecks of gore.  She hit the ground and her momentum carried her forward, skidding.



Chevalier didn't flinch as she hurtled towards him.  Instead, he waited until her trajectory brought the right part of her into harm's way, then shot out more of her limbs.  The impact of the hit brought her to a halt, spinning until her back was to him, only two of her monstrous claws intact.



A female hero threw out small ice crystals in Echidna's direction, and they expanded explosively into virtual glaciers on impact.  Maybe the intent was to give Echidna less room to regenerate.



Chevalier withdrew the twenty-five foot long blade from the ground and chopped at Noelle – the upper body that jutted out of Echidna's back.  He severed her from the monster at the stomach, turning the blade mid-swing to catch the body on the flat of the weapon. He swatted her away, separating the girl from the monster.



The impact of Noelle's landing was enough to kill, but she didn't die.  She flailed weakly for long seconds before she started falling apart.



Echidna caught Chevalier with a tongue.  He cut the tongue with his blade, and walked around her, blade poised, as if he were trying to find a place to strike.



I realized he was trying to find a way to rescue the people inside.  Alexandria, Eidolon, and seventeen of the capes who'd volunteered to fight this thing.  Had he directed the cannon blast with the same intent?  To avoid harming the people within?



Chevalier was struck.  He turned, and was hit again.  He was under siege from one of the nigh-invincible clones, with the burning hands.  The guy was digging his hands into a car at one side of the street, coming up with hunks of white-hot metal and flinging them.



He scraped them off, but more attacks were incoming.  One cape threw a stone, and though the speed and arc of the thrown rock didn't seem to amount to much, it shattered one of the glaciers the ice-cape had erected.



Chevalier used his cannonblade to block another rock and a lump of molten metal from striking home.  From above and behind him, the woman with the ice shards began raining her attacks down on the clones, encasing them in ice.



I joined in, sending my swarm forth into the fray.  They flowed from the battlefield around me, finding paths to travel between the crags of ice and the capes.  Cockroaches tore into the membranes of eyes.  Hornets found flesh to bite that was close to arteries and veins, stings dug into the most sensitive flesh, and ants worked together to scissor and tear flesh more efficiently.



More bugs moved in the Eidolon-clone's direction.  The flying insects faltered, their usual mechanisms for movement failing them.  Then they started falling out of the air.



They were suffocating; it was a vacuum.



He'd chosen his powers, and by the looks of it, he'd dressed himself in a mirror of his other self's costume.  A costume with a black hood, loose black sleeves and a pale red-orange glow emanating from each opening.



The flickering.  Was that some variant on Scapegoat's power?  More broad?  Paging through realities to find the \emph{state} he wanted to be in?  Uninjured, dressed?



There were a lot of ugly possibilities with that one.  Could he affect how he was accessing powers?



He took one step, and was carried off the ground.  It wasn't flight so much as \emph{floating}.  Combine that with the vacuum around him\ldots It had to be aerokinesis.  Manipulation of air.



Miss Militia took a shot at him, and he reeled.  There was a flickering, and he was back in the position he'd been in a moment before, uninjured.



She changed guns, and unloaded two assault rifles in his direction.



Her hits were on target- at first.  His armor absorbed the worst of it, and he undid the damage he'd taken with more flickering.  The bullets gradually moved off target, grazing him instead of striking vital areas.  A moment later, they stopped hitting entirely.



The effect he was using to alter their trajectories hit the rest of us a moment later.  I felt Atlas's wings beat against nothing for just a moment before we caught air again, steered him through a sudden, unexpected headwind that dissipated as fast as it had started, and then found a spare moment to pull up, putting distance between myself and the Eidolon clone.



My bugs gave me a sense of his effect's perimeter.  The storm effect had a diameter of roughly three-quarters my own range, no doubt allowing him to sense where people were by the movements of the air.



The vacuum extended roughly a hundred feet around him, the air condensing into threads that found him and flowed into his mask to sustain him.  Even the clones on his side were suffering, falling to their hands and knees or running to get away.  He was indiscriminate, and far more dangerous because of it.



He was approaching the battlefield where we'd engaged the clones, where many of our heroes had fallen.  If the vacuum extended over them, they wouldn't last long.  I wasn't sure what kind of effect it would have, but even the smallest push could mean the difference between life and death, and this wasn't necessarily small.



``Rachel!'' I shouted, but the wind kept my voice from reaching anyone.  It didn't matter.  I could use my bugs, too, not as a collective effort, but with ten thousand voices in a hundred ears.  ``\emph{Rachel!  Get over here and fetch the wounded!  Everyone else!  Get your teammates back!  He's surrounded by a vacuum!}''



Heroes kicked into action, hurrying to collect the injured.  Rachel was occupied trying to herd the clones at the far edges of the battlefield, but she heard my order and broke away from the skirmish.



We still had to manage those clones, though.  A few Kudzu, and none of the forge-guys.  If they got away-



I contacted the ice dispenser.  She was trying to cover Echidna in more ice, but the wind was blowing the shards away.  ``\emph{Need your help to contain clones.  This way}.''



My bugs pointed the way.  She hesitated, tried to shout something to Chevalier, but went unheard.  She decided to follow my instruction, flying in the direction I'd indicated with the bugs.



Okay, so she was one of Chevalier's people.  I told Chevalier, ``\emph{Your ice cape is dealing with clones.}''



He only nodded.  He at least knew she didn't have his back, now.



People were moving too slowly as they dragged and carried teammates away.  Worse, there were only so many able bodies.  Only three or four out of every ten heroes were down, all in all, but some required two people to move, and there were those like Tecton that required enhanced strength to budge.  Eidolon was getting dangerously close, now.



People screamed and shouted in alarm as Rachel reached the fallen.  She barely paused as she stopped momentarily by each body, pointed, and screamed the name of one of her dogs.



``\emph{It's okay,}'' I communicated, though it was getting harder with what Eidolon was doing with the air.  ``\emph{Rescue operation only.}''



The dogs followed her instructions as much by mimicking Bentley as by anything else, it seemed.  I knew they weren't well trained, and there was a reason she didn't bring these dogs on every excursion.  It would look bad if we killed a hero in the process of rescuing them, but we were risking that simply by moving the wounded.  It had been reinforced over and over in the first aid class I'd taken, never to risk moving anyone who was injured.



Then again, this wasn't exactly a typical situation.  Better to remove them from near-certain death.



With Rachel rescuing the wounded, the Eidolon-clone didn't have any easy targets in reach.  Instead, he turned and floated toward Echidna.  Ice was chipped and whittled away by what must have been sharp blasts and currents of condensed wind, with fragments flying toward him, twisting in mid air and whipping back at the chunks of ice they'd come from, helping to chip away.  Enough cracks formed that Echidna could use her two remaining limbs to leverage herself to her feet.



The meaty, frost-crusted ruins where her legs had been blown away by Chevalier were healing over, bulging where muscle and bone were growing within the stump.  Bone penetrated the flesh where her claws and armor were.



And on top, Noelle was already more or less regrown, her arms wrapped around her upper body in a straightjacket of flesh, her eyes closed and face turned toward the sky.



Chevalier took aim and shot, and the cannonball veered in midair, slamming into Echidna instead of Eidolon's clone.  One of Echidna's growing limbs was destroyed, but so was the glacier that had encased it.



The Eidolon hit Chevalier with a focused blast of wind, and the hero went flying, the air in the Eidolon's range shifting to reduce resistance and carry him further.



Chevalier was out of my range before he hit ground.



Legend and Alexandria still fought above us.  I could, when he passed into my range, note how he got faster the longer he flew, giving him the ability to put distance between himself and Alexandria, but he couldn't stop to take aim and shoot without losing that acceleration and giving her a chance to close the gap.



The result was that he was flying in loops and circles, using the turns to find opportunities to take aim and fire on her.  She dodged most, but the hits that did land bought him distance and time to stop and laser down clones who were attempting to escape.



If any of them slipped away, it could be disastrous.  One clone could track down their original self's family and murder them, or even go after innocent civilians.  My bugs were blinding them, finding weak points, but there were some that my bugs couldn't touch that Legend was succeeding in taking out, like the forge-man.



Myrddin was below Legend and Alexandria, recuperating from holding Echidna at bay.  He took to the air, flying up to Echidna and the Eidolon-clone from behind.



He pointed his staff at the Eidolon, and his target disappeared.



The air the Psycho-Eidolon had compressed expanded all at once, sending Myrddin flying off course and Echidna rolling sideways, over a line of parked cars.  For the moment, the vacuum was gone.



Myrddin set himself down on the ground.  He wasn't using his power against Echidna or the clones, which suggested that his reserves were low.



The Eidolon-clone reappeared.  He turned and spotted Myrddin.  The two started fighting, the Eidolon trying to close the gap and trap Myrddin in his vacuum, which was considerably smaller in area than before, but growing every second.  He hampered the self-professed wizard's flying with headwinds and gusts, and sharp blasts of wind that Myrddin deflected or dodged.  Myrddin, for his part, attacked relentlessly, pummeling the Eidolon with explosions of energy alternating with scattered releases of whatever he managed to suck in while close to the ground.



Echidna was mending, and with Chevalier down and our heavy hitters more or less out of the running, I wasn't sure we could stop her.



We needed to stall.



One tinker had machines rigged on the ground, with forcefields erected in layers, one behind the other, five between himself and Echidna.  I'd glimpsed him at work before, knew it wouldn't hold if she \emph{really} hit the things.  They were dangerous or lethal to the touch, if the experiences of my swarm was any indication, but little more than an annoyance for Echidna.



The ice cape was back, having dealt with the clones.  She began laying down more glaciers around Echidna, but with the monster being more able-bodied than before, it was only a temporary barrier.



We needed something more effective.



My eyes roved over the fallen, both those that had been rescued and the ones that still lay on the ground, injured or dead.  Weld had Kid Win and Scapegoat, and I recognized Browbeat dragging Tecton behind him.  He must have joined another team in another city, only to find himself accompanying them in a return trip to Brockton Bay.



No.  This wasn't a case where we needed brute force.  Echidna was liable to win any case of hand-to-hand combat that wasn't against a full-on Endbringer.



Maybe she could even come out ahead in a close-quarters fight against the likes of Leviathan or the Simurgh, if she was capable of absorbing them.



Scary thought.



I recognized so few of the capes around me.  There was a girl who was emanating red lightning that wasn't harming the allies she struck, apparently accelerating them to a faster speed instead.  I had seen her \emph{somewhere}, but had no idea who she was.  A boy was fading in and out of reality, grabbing capes and then disappearing with his rescuee in tow.  He'd reappear a moment later, a few paces away, before fading out of existence.  He wasn't teleporting, he merely wasn't \emph{here} when he was walking, some of the time.



Rachel arrived with a number of fallen capes in tow.  I flew low to the ground and helped lower them to the nearest solid surface.  One dog had bitten too firmly, not knowing its own strength, cracking body armor and maybe a rib.  I didn't mention it – it was obvious enough that people would catch on before he was in terminal danger, but we didn't need people turning on Rachel or getting distracted from the matter at hand.  The man was alive, and that was better than if he'd been caught in the vacuum.



Psycho-Eidolon went on the offensive against Myrddin, shoving the hero against a wall and then holding him there by pummeling him with repeated blasts of wind.  The Eidolon got close enough to catch Myrddin in the vacuum, and the bugs I had on Myrddin started to perish with surprising speed.



Myrddin, for his part, stopped fighting entirely, trying only to escape.  The Eidolon caught him and knocked the staff from his hand, then pinned him against the wall, choking him with the vacuum.  I knew it was supposed to take around two minutes to suffocate, but that presumed one was able to hold some air in their lungs.



Myrddin's struggles were getting weaker by the second, almost from the instant he was in the Eidolon's range.



The Eidolon's grip slipped from Myrddin's neck and he careened into the ground, hard.  Again, air billowed out around him, thrusting Myrddin into the wall once more, but supplying him with much needed air.



I could see Regent, turned towards that particular bout of fighting.  Had he been responsible?



It wasn't enough to revive Myrddin.  He fell to the ground, only a short distance from the Eidolon, and slumped down into a prone position.  One hand pressed against his chest, and he went limp.



The Psycho-Eidolon stood, and Miss Militia opened fire, joined by several other capes.  The Eidolon was driven back, forced to flicker to recover from the blasts.  Again, his armor was absorbing the impacts.  It would be the best stuff money could buy, if it was a functional copy of what his other self wore, and it was healing every time he did.



Then, as before, he found a way to divert the incoming fire away from himself.  The bullets and laser blasts stopped, no doubt because the heroes didn't want the Eidolon redirecting any of their fire towards Myrddin.



My bugs flowed in, carrying a length of cord.  I bound the Eidolon's neck as he walked up to Myrddin's unconscious form, but there wasn't anything significant to tie the cord to.  I chose a car's side-mirror.



He stopped short, a pace away from the fallen hero, then flickered.  The cord came free of his neck as though he weren't even there, and he bent down over Myrddin.  I swore under my breath and tried to bind him again, knowing how ineffectual it would be at this point.



It was Wanton who moved to stop the Eidolon, turning into a virtual poltergeist, with debris and dust flying around him.  He barely slowed as Eidolon directed a blast of wind his way.



The Eidolon flickered, and a knife with a wavy blade appeared in his hand.  Before Wanton could reach him, he gripped Myrddin's mask, raised the hero's chin towards the sky, knife held ready.



His hand convulsed, and he dropped the knife.  Regent.



An instant later, he flickered, rendering his hand untouched, the knife back in position.  He thrust it into the soft underside of Myrddin's chin.



Wanton hit him a moment later, tearing the dagger from the Eidolon's hand and using it to cut and bludgeon the clone.



Myrddin was dead or dying, I couldn't even guess if Chevalier was okay or not, and two of the three members of the Triumvirate had been turned against us.  We were swiftly running out of big guns.



The red lightning girl hurried past me, helping mobilize a group of heroes with more wounded.  We had maybe forty to fifty capes on our side, with twenty that were no longer in any shape to fight.



I saw Gully with two heroes cradled against her body with one arm, the other arm holding her shovel, planting it in the pavement like it was a walking stick.



One of the heroes was Clockblocker.  The face of his mask had been shattered, revealing the softer padding beneath.  I didn't recognize the other cape, a guy with green dyed hair and a domino mask.



``Stop,'' I told her.  ``Is he okay?''



``Ramus is, but I think the clock boy is going to die,'' she said.  She glanced over her shoulder at the Psycho-Eidolon.  He'd broken away from Wanton, and was working on mending the damage, one part of his body at a time.



If there was a limitation to his self-heailng, it was that.  It was healing by degrees, weaker against all-around damage.  If my bugs could have gotten to him, that might have done some damage, but they'd have to get past his armor, which looked like the all-concealing sort, and there was the not-insignificant matter of the vacuum.



``Clockblocker,'' I said.  ``You there?''



He turned his head toward me.  I could barely make him out over the wind.  ``You're still here.''



What did he mean by that?  Was he surprised that I was still alive?  That I hadn't run?  I wasn't sure how to respond.



``\emph{Craved a fight},'' the words reached me despite the winds that were tearing across the battlefield.  It wasn't my bugs speaking, either.  ``\emph{I hoped you'd challenge me.}''



Eidolon.  He was echoing his sentiment from earlier, that had driven him to fight Echidna alone, except it was twisted, warped, the original reasoning forgotten.



``\emph{Do I need to get you angrier?  Do I need to push you harder?  I could torment you, inflict pain on your teammates until you're forced to throw all caution to the wind and come at me with everything you've got.  Or I could attack you on another level.  Would you like me to tell you a story?}''



Echidna belched out another set of clones.



There was one forge-man, two identical to the one I'd seen flinging stones at Chevalier.  And an Alexandria.  They lurched to their feet, but they didn't attack.  They were letting Eidolon speak.



``\emph{We founded Cauldron.  The Triumvirate.  The Number Man.  William Manton.  The Doctor.  We sold people powers.}''



``No,'' Clockblocker said.  Other murmurs came from the crowd.



``\emph{It meant more people with powers to fight the Endbringers, that was the lie we told ourselves.  But we created the Siberian and Shatterbird, in a roundabout way.  We created the Gray Boy, selling him powers, finding ourselves unable to stop him when he went out of bounds.  There were countless others.  Echidna is just the latest in a long series of grave mistakes}.''



Nobody moved.  I suspected that if anyone attacked him, they'd be seen as a Cauldron sympathizer, trying to shut him up.  I could see Noelle: her arms had separated from her torso, but she left them limp at her sides, her long hair in her face as she stared up at him.



``\emph{We made the PRT, pretended to let ourselves be run by the unpowered, but we put Alexandria in charge.  We manipulated media, manipulated nations, in the interest of power.  We ventured into alternate worlds to kidnap people, experimented on them to refine our formulas.  And the failed tests?  The people who turned out wrong?  We cast them out, tossed them out as a bonus to anyone willing to pay a little more for an enemy that was guaranteed to lose against them}.''



The Eidolon moved, facing one of the monstrous parahumans I didn't know.  A boy with crimson skin and hair.  The clone spoke, ``\emph{That's all you were, monsters.  Little more than the cheap towels that are on offer for a few extra dollars when you buy something on a shopping channel.}''



Legend shouted something, but the wind kept his voice from reaching us.  He had to fly to avoid the Alexandria-clone's unending pursuit.



The other, naked Alexandria took flight and went after him.



It said a lot that nobody moved to help.



I glanced at Gully, saw her already disfigured face contorted with emotion.



``He's lying,'' I said, to her.  ``Twisting the truth to make it sound worse than it is.''



Gully only made a small noise in response.



``He couldn't make all that up,'' Clockblocker said.  Were it not for the bugs I had near his mouth, I wasn't sure I would have caught what he was saying in the face of the wind.  ``\ldots kernel of truth.''



``\emph{It's all been a ploy from the start,}'' the Eidolon-clone said, his aerokinesis carrying his words to our ears, ``\emph{Every single one of you were deceived.  For every one of you that bought your powers, there were innocents who died or became monsters for the sake of that formula's research.  No matter what good you might do, it will never make up for that.  And the rest of you?  Conned, brought in with promises of ideals and saving the world.  You're fools.}''



And with that, he let the wind die down.  There was a crunching noise as Echidna shifted her weight, but that was followed only by silence, the sound of murmurs.



``We just lost,'' Clockblocker said.



I looked at him, saw Gully hanging her head.



He wasn't wrong.  We were suffering losses, and we hadn't achieved anything.  Echidna was as strong as she'd ever been, stronger than she'd been at the outset of the fight, and she kept on acquiring clones that cost more than we could afford to put down.  Alexandria and Eidolon were only the tips of the iceberg.



``It's a big hit to morale, but-''



``No,'' Clockblocker cut me off.  ``We \emph{lost}.  Not this fight.  Maybe we can still win it, won't deny it's possible, with Scion maybe showing up.  But the big picture?  There's no coming back from this.  Without the Protectorate, without all the work that it does to organize heroes around the world, there's no getting everyone working together.  The amount of \emph{anger}?  The \emph{suspicion, }wondering if a teammate took the formula or not?  How can we go up against the next Endbringer that shows up?''



``We'll manage,'' I said.  ``We'll find a way.''



He barked out a cough, groaned.  ``Fuck, don't make me laugh.''



``Laugh?''



``Never took you for an optimist.''



Was I?  Or was it just that the heroes were reeling just a little more in the wake of these revelations.  I wasn't surprised, and I was betting the other Undersiders weren't either.



Advantage: us.  We villains were the only ones who could really think straight in the wake of all this.  Except Tattletale, Grue and Imp were elsewhere, and Regent and Rachel weren't really in a position to do anything major here.



I stared at the scene, Legend doing his best to fend off two Alexandrias, and Eidolon looking down on us, the crowd of fools.  I could see Echidna, standing still, surveying it all, much as I was.



No, not Echidna.  \emph{Noelle}.



``I need your help,'' I told Clockblocker.



``Can't fight.''



``Don't need you to fight,'' I told him.  I reached behind my back, drew my gun.  I pressed it into his hands.  ``If and when she comes for me, aim for the back of my head.  It's unarmored, anything else might mean I survive, and I don't want to be \emph{hers}.  Not again.''



``Hers?'' he asked.  ``What are you doing?''



I paused.  ``Wait until the last second.  Just in case.  You can call that more optimism, I guess.''



``Skitter?''



I moved my bugs away from the heroes around us and into the air, a cloud capable of getting attention.



If I was going to do this, I was going for optimal effect.



Back when this skirmish had started, I'd wondered if I'd be willing to make a sacrifice if it meant coming out ahead.  Even when the idea of throwing away one life for the greater good had crossed my mind, it had been with the notion that it would be \emph{me} paying the price.  I couldn't, \emph{wouldn't}, ask someone else to do it.



Fuck it.  I wasn't about to back down now, not with the stakes this high.



With the swarm swirling through the air, and the fact that I was the only person moving in this otherwise still tableau, all eyes were on me.  Noelle's included.



``Noelle!'' I screamed her name.  My swarm augmented my voice, carrying it much as the wind had carried Eidolon's.



She turned toward me.



``It \emph{is} you, isn't it?  It's Noelle, and not Echidna?''



She didn't respond.  My swarm drifted between us, partially to help obscure me, to cloak me from her vision if she charged me.



``At the start of all this, you offered a deal.  Any of your captives for one of us Undersiders.  Is that deal still open?''



I saw her shift position, planting her massive claws further apart.



``You're dead anyways,'' she said.



\emph{You're not wholly wrong}.



``Follow through with the deal, maybe you get to kill me yourself.  And maybe the other heroes here will turn the other Undersiders in for a chance that they can walk away alive.''



``You're saying you'll let your team die?''



``My team can fend for themselves,'' I said.  ``Right now?  I'm offering you \emph{me}, in exchange for Eidolon.  That's all.''



``The one who deceived \emph{them}?'' she looked out over the crowd.  ``What makes you think they \emph{want} him?''



``They don't,'' I said.  I made sure that everyone present could hear as my bugs carried my voice.  ``But they \emph{need} him.''



If there was any salvaging this, any way of recovering from this terminal hit to morale and avoiding the scenario Clockblocker had outlined, I had to make sure that everyone recognized how essential it was that we kept the big guns on hand for future Endbringer attacks.  Regardless of what they'd done in their pasts.  If it came down to it, I was willing to put myself on the line.  I'd die to drive the point home if it came down to it.



Noelle spat Eidolon out.  He landed, covered in puke, wearing his costume.  He recovered faster than the other heroes had, faster than I had.  He took to the air, flying toward the other members of the Protectorate.



A pair of flying heroes moved closer together, barring his path.



Through the bugs I had placed on the two flying heroes, I could hear him.  A single utterance, monosyllabic.  ``Ah.''



He turned, surveying the scene, then started to fly towards Legend.  The other Eidolon moved to match his flight, and the original stopped.  If he moved to help, he'd only be bringing his clone into the fight with him.  He settled above a building, on the other side of the street from his mirror opposite, keeping a wary eye on Legend and the chase that the two Alexandria clones were giving.



``Now's the part where you run,'' Noelle told me.



``I'm not running.''



``You'll try something.  Because you're a coward.  You don't have it in you.  You're selfish.  You killed Coil when you knew \emph{we} needed his help.''



``I killed Coil because he was a monster,'' I said.  I didn't let my voice carry, but it didn't matter.  Others had heard what she said.  ``But I'm not running.''



I sensed Rachel kick Bentley, stirring him to action.  Some of my bugs barred her path, forcing her to pull short and stop before he'd moved two paces.



``How do I finish you, then?'' she asked.  ``Should I puke on you and let them tear you apart while everyone watches?''



``Someone might try to save me,'' I said.  ``They're still heroes, after all.  Takes a lot to stomach watching a girl get beaten to death.''



``Then I kill you myself,'' she said, and there was a growl to her voice.  That would be Echidna chiming in, at least in part.  ``They'll see what you're made of when you break and start running, and they can't stop me from tearing you apart.''



That said, she charged.  The ground shook with her advance, and the heroes only stood and watched, no doubt considering the possibility that I was right, that they could negotiate their way out of all this.



I closed my eyes, using my bugs to stop Rachel from intervening for the second time.



I took a deep breath.  Every instinct I had told me to run, to find shelter, to survive, or take cover.  But I had to do this.



Instead, I used my bugs to whisper to Clockblocker, ``\emph{Use your power}.''



There was only one thing for him to use his power on.  He froze the gun.  Along with the gun, he froze the length of thread I'd attached to the weapon.



The thread, in turn, was held aloft by the bugs that flew as a curtain between Noelle and I.



I kept my eyes closed, relying on my bugs to feed me input, dissociating from my real self, because it kept me still, and \emph{that} kept Echidna on course for the thread that extended vertically through the curtain.



Spider silk was, generally speaking, about two to three times as thick as the thinnest part of a safety razor.  That was still pretty thin, especially when Clockblocker's power rendered it immobile, utterly unyielding even as a monster with three times the mass of an African Elephant crashed into it.



She tried to pull to a stop as she made contact with the thread, but her momentum carried her all the way through.  The bracing of her foremost limbs against the ground only helped to force the separation of the two halves.



Severed, the two pieces of her body crashed down to either side of me.  Despite my best intentions, I stumbled a little at the impact.



``\emph{Hit the Eidolon-Clone},'' I spoke to Miss Militia through my bugs, hurrying to step away from Noelle's bisected form.  ``\emph{Hit him hard.}''



The Eidolon-clone moved one arm in our direction, only to stop short.  A thread that had draped his arm was now a rigid barrier, connected to the same thread that I'd positioned between Noelle and I.  He tried to retreat, only to find the thread I'd circled around his neck holding him firm.



He started to flicker, no doubt to escape.  One arm free.  Then another.



Miss Militia hefted her rocket launcher.  \emph{Our }Eidolon was already flying to Legend's rescue as she pulled the trigger.  The Eidolon-clone wasn't quite free when the warhead hit home.  For extra measure the explosion drove him against the threads that had draped his body.



If I'd been good at the punchlines, I might have thrown one out there.  The best I could come up with was, \emph{Flicker that}.



``\emph{Watch the two pieces,'' }I communicated through my swarm, still backing away from Noelle.  ``\emph{Tattletale said there's a core to her, that's supplying the regeneration.  Whichever half regenerates is the half with the core.  We narrow it down, then we destroy it.  We can win this.}''



I could see Echidna's body swelling, growing huge with tumorous bulges as she sought to rebuild her other half.  Still, she was nigh-immobile, and the heroes were free to unload every offensive power they had on her.  Wanton and Weld advanced, tearing into her, pulling people free and seeking something that might be her core.  She was regenerating faster than they were dealing damage, but every passing moment saw one cape freed, more ground covered.



Her other half was decaying at the same time.  The captives that were trapped in her flesh were revealed as it dessicated, and capes freed each person in turn.



She lurched, then forced herself into contact with her decaying other half, reconnecting to it.  She was minus eleven captives, by my count, Alexandria among them, but she was reforming.  I wouldn't be able to bait her like that again, but I might be able to contain her.



I glanced at Clockblocker.  Gully had carried him to Scapegoat, who had roused from unconsciousness, and he was getting care.  He looked at me, offered me a curt nod.



I wasn't sure how to respond, so I did the same.



Behind me, bugs could sense the approach of a containment van.  Tattletale, I could hope, with Faultline's crew, perhaps.  Chevalier was perched in the fortified turret on top, his sword resting on one shoulder.



\emph{We can win this fight}, I mused, and this time I could believe it.



But I was all too aware of the movement of a particular contingent of capes.  Having deposited Clockblocker, Gully distanced herself from the other heroes, approached Weld and the red-skinned boy.  The Cauldron-made, standing apart.



Across the battlefield, I was aware, there were very few people standing shoulder to shoulder.  People were distanced from one another as though their personal space was ten feet across, avoiding eye contact, with no conversation, and I wasn't seeing any upturn in morale.  There wasn't a cheer to be heard, and squad leaders weren't giving orders to their subordinates.



I could only hope \emph{this} divide wouldn't prove as telling as the one I'd delivered to Noelle.





