





The heroes found positions and opened fire on Echidna.  The difference in \emph{this} and the fighting as it had been before was noticeable.  Small, but noticeable.  Capes weren't communicating and teamwork was faltering as a result.  Capes like the red lightning girl and Chronicler were struggling to find people to use their powers on.



I didn't want anyone else running or flying headlong into the thread, so I gathered my more harmless and useless bugs in a thick cluster around each piece of thread, until each thread appeared to be a black bar a half-foot across.



Clockblocker appeared at my side.  He was in fighting shape, though he didn't look it with his damaged costume.



``Anything I can do?'' he asked.  ``Anything else set up?''



I shook my head.  ``She dissolves the thread if it touches her flesh, and things are too frenetic.  Someone would get hurt.''



``Gotcha,'' he said.



He didn't move from where he was standing.  A minute passed as Echidna was bombarded.  She wasn't quite at full fighting strength, she didn't have many capes to clone, and she was apparently hesitant to charge or make any sudden movements with the possibility of there being more thread.



``Why didn't you tell me?''  Clockblocker asked.



``That I had something in mind?'' I asked.  ``I guess a part of me thought that maybe if you figured out what I was doing, you wouldn't have frozen the gun.''



``That's not fair.  I don't think I've given you any reason to think I'm vindictive like that.''



``Not really,'' I admitted.  ``Maybe I didn't want you to give her a tell, or do something that Eidolon might notice.  I'm not sure why, not entirely.''



``So you're not really doing anything that those guys out there aren't.  When it comes down to it, you're suspicious of us, just like we are of each other.''



``Maybe,'' I admitted.  ``It's\ldots a lot to take in.  What do you even do from here on out?''



``I don't know,'' Clockblocker said.



A series of neon green concentric circles exploded outward from a point in the sky above, rippling out to disappear over each horizon.  Eidolon had engaged one Alexandria-clone, and whatever he'd done seemed to have finished her off.  One left.



Echidna belched out a mass of clones, and I added my bugs to the firepower that the heroes threw their way.



Some slipped past the loose perimeter the heroes had established, and were promptly gunned down.



``I'm guessing Tattletale told you the particulars of my power?'' he asked.



``What do you mean?''



``The range?  I'm surprised you knew it would work through interconnected pieces.  Hell, \emph{I} barely knew I'd be able to push that far.  I guess that makes this one of the rare days my power's working at peak efficiency?  But you somehow knew that?''



I glanced over my shoulder at Tattletale.  She was getting out of the van, and was joined by Faultline, Labyrinth, and four members of the Travelers: Sundancer, Ballistic, Genesis in her wheelchair and a blond boy who resembled but didn't quite match Oliver in appearance.  Tattletale was exchanging words with Regent.  Getting an update?



``You're not responding,'' Clockblocker noted.



``I''m not sure what you want me to say.''



``\emph{Yes, Clockblocker,}'' he added a falsetto note to his voice, bent one wrist to a ninety degree angle as he raised his hand to his mouth, ``Of course \emph{we know more about how your powers work than you do.  How else would we kick your posteriors with such frequency?}''



He faked a high society woman's laugh, where the laugh was \emph{said} as much as it was uttered.  A cape nearby, one I recognized as Astrologer from the New York team, shot us a dirty look, before she returned to calling down projectiles from the sky.



``I don't sound like that,'' I commented, trying not to sound as irritated as I felt.



``I thought it fit pretty well for one of the wealthy crime lords of Brockton Bay,'' he said.



I was a little caught off guard, to see this side of Clockblocker, or more that he was showing it to \emph{me}.  Was it humor as a coping mechanism?  Or \emph{attempted} humor as a coping mechanism, to be more on target?  I could believe it, from the guy who'd chosen \emph{Clockblocker} as his cape name.  But to let me see anything other than the hard-nosed defender of the peace was something different.  A show of trust, letting his guard down some?



Or maybe it \emph{was} just a coping mechanism, and he had a hell of a lot to cope with.  Only an hour ago, he'd probably felt he had his whole future laid out for him, a career in the Wards transitioning into a career with the Protectorate, with funds, fame and every side benefit and piece of paper he might need to mask his real identity.  Now nobody had any idea how that would work out.



Another circle exploded across the sky.  Alexandria-clone-two was down.  Legend and Eidolon descended in Echidna's direction, keeping a healthier distance.



Whatever Eidolon had been hitting the clones with, considering the area it was covering and the fact that it was apparently taking \emph{Alexandria }out of action, it suggested a kind of attack that couldn't be used near the ground, because it might have leveled whole sections of the city.



Tattletale caught up to me.  The others in her retinue hung back.



``Was that you two?'' she asked.  She pointed at Echidna, where the right and left sides of the monster's body weren't quite lined up.



``Yeah,'' I said.



``You realize that if you pull off the dramatic sacrifice, Grue won't be able to take it?  He's relying on you to be his crutch for the time being.  You can't kick it out from under him mid-step.''



``He's stronger than you're saying,'' I murmured.  I eyed Clockblocker, all too aware that he was listening in.  Tattletale was aware, too, which meant she was trying to communicate something.  ``Can we finish this discussion elsewhere?''



``Why don't I just leave you alone?'' Clockblocker offered.  ``I wanted to make myself available in case you wanted to repeat the maneuver, but you're saying that's not so doable.''



``Not really,'' I admitted.  ``But thank you.''



``Signal me if you need me,'' he answered.



Alexandria had a steel, fire-scorched girder in her hands, retrieved from a fallen building nearby.  She wasn't flying, but she walked forward, relying on the girder's size and sheer \emph{presence} to clear her way through the assembled capes.



Her back was straight, her chin raised, as her subordinates stared.  Her black costume, it was fortunate for her, served to hide the worst smears and stains from Noelle's vomit.



She swung the girder at Echidna like someone else might swing a baseball bat, and Echidna was knocked off her feet and into a building face.  The girder didn't bend like the traffic light had.  This was a piece of metal intended to help support \emph{buildings.}



Echidna opened one mouth, no doubt to vomit, and Alexandria flipped the metal around, driving one end into the open mouth and through Echidna, the other end spearing out of the monster's stomach.



Before Echidna could react or retaliate, Alexandria flew straight up into the air, joining Legend and Eidolon.



As attacks went, it wasn't a game changer.  Something else?  A symbol?  A gesture to \emph{us}?



Echidna roared, lunged, only to hit a forcefield.  The field shattered and she stopped short, the girder rammed further through her.



To say we were at full strength would be a lie.  Too many had been injured.  Still, we'd pinned her down.  I could see Noelle atop Echidna's back, craning her head to look at me.  Through some signal or some shared knowledge, Echidna was following Noelle's recommendation, avoiding sudden movements, enduring every attack that came her way rather than risking running headlong into more frozen silk.



In fairness, she still had something of an upper hand.  None of our attacks were slowing her down, not really.  She was healing faster than we hurt her, and our side was getting tired, burning resources.  We weren't sustaining casualties, but we weren't winning this fight either.



With our current disorganization, it was only a matter of time before she popped out \emph{another }clone that was capable of turning the tables.



``We need to finish her,'' I said.



``Sundancer could do it, probably, but she would need convincing.  Labyrinth's going to set up while we wait for Scrub,'' Tattletale replied.



``Where is he?''



``Bit dangerous to have him riding along in a car.  We put him in another, and he nuked the engine.  We rigged a sled, and he should arrive in a bit, depending on how many times they need to stop and replace the chain,'' she said.



``He's going to open the door?''



``\emph{Open} is probably the wrong word.''



``What's the right word?''



``I'd say it's more like using a battering ram than a doorknob.''



``With \emph{dimensions},'' I said.



``\emph{Through} dimensions.  Knocking down the door, not knocking down the house.''



``I'm not seeing the difference between the two,'' I said.  ``What's to say a given area is one thing over another?''



``\emph{That},'' Tattletale said, ``Is Labyrinth's job.''



I could see Labyrinth.  Faultline was right next to her, apparently talking her through the process.  Arches and high walls rose like cresting waves, locking into place as they met one another.  It amounted to what looked like a church, if only four paces in diameter.



``You think that'll be easier for Scrub to punch through.''



``Positive,'' Tattletale said.



``How do you punch through to the right \emph{place}?''



``\emph{That}, Tattletale said, ``is something we'll have to trust to luck and an educated guess.''



``Not reassuring,'' I said.  ``What's going on?  I'm worried.  Nearly getting yourself shot, \emph{twice}?  Provoking the Triumvirate?  Spending however much it costs to bring Faultline into the city, after the financial hit you took pulling the soldier gambit on Coil?  Now this?  The dimensional hole?''



``It's how I operate.''



``Yeah, you've been reckless before, got cut by Jack, provoked Glory Girl.  But this is turning the dial to eleven.''



``We came out ahead in the end, both times.''



``It wasn't necessary.  There were other ways around either of those situations.''



``Not as much as you'd think,'' Tattletale said.



Echidna roared again, each of her mouths making a slightly different noise, combining into a discordant noise that made almost everyone present wince.  Weld tore his way free of her side, two capes in his grip.



\emph{Still five captives inside}, I noted.  I saw Weld climb free and drop to the ground.  He wasn't going back in for more.



Tattletale took me by the arm and led me back and away from the fighting, to where we had more privacy to speak.  I used bugs to guide some capes at the back lines toward some clones who'd flown into an alley.  It was odd, to be playing a part in a high-speed chase while standing still, but the capes were closing the distance on their quarry nonetheless.



``I'm just looking for answers,'' I told her.  ``This dimensional hole, provoking the heroes, apparently spending a lot of money I'm pretty sure you don't have.  I\ldots I can kind of \emph{get} that you're feeling a bit aimless, a bit unfocused.  Maybe that comes across as recklessness.  I'm feeling like that too.  We beat Coil, and so much of what we've done over the past while, it was with the end goal of doing just that.  So I \emph{get} if you're not sure of where to go from here.''



``Except you've been talking to the heroes, and you've had that to help center yourself, figure out where you stand,'' Tattletale said.  ``I haven't.''



``That's it?  You need to \emph{talk} to someone?''



``No.  That's not what I'm saying,'' she said.  She sighed.  ``Yes.  Kind of.  It's only part of it.  Who the hell am I going to talk to that grasps things on a level I do?  Do you really expect me to find a therapist and sit down and \emph{not} pick him apart faster than he can decipher me?''



``You could talk to \emph{me},'' I said.



``Not when you're part of the problem, part of what I'd need to work past.''



``That's not fair,'' I told her.



``No, it isn't,'' she admitted.



Echidna spat out volumes of clones at the defensive line.  The reaction was only a \emph{little }slower than it should have been.  Squads still weren't operating as squads.  Legend and Eidolon were offering support fire from above, but they were standing apart from the rest, in a much different way than Tattletale and I were.



``It's not you,'' Tattletale said.  ``It's more about my relationship with you.''



``This isn't the point where you confess your undying love for me, is it?''



She snorted.  ``No.''



``Then what?  Or is this just going to be another secret you keep?''



``All of the good secrets are getting found out anyways, or so Regent said.  I suspected they would be, for the record.  Part the reason I dished like I did was to put us in a good position in case the juicy stuff \emph{did} come out.''



``Not sure I buy that,'' I said.



``You don't have to.  It was only a part of it.  And I understand if a more in-depth explanation is overdue, but I need to turn it around in my head some, get it to the point where I can share it without it coming out wrong.''



``Your trigger event?'' I asked.



``That's a part of it.  But can we please put that off until \emph{after} we've torn a hole in reality and stopped the pseudo-Endbringer?''



``Just tell me this isn't another educated guess.''



``It's not.  Except for the bit where we might be able to find the right universe.''



``When you're saying it's not an educated guess, is that because you're \emph{sure} or because it's an \emph{un}educated guess?''



``I'm \emph{mostly} sure.''



I sighed, loud enough for her to hear.



She grabbed my hand and pulled me in the direction of the van she'd brought.  Labyrinth's church had expanded considerably, and Scrub was very deliberately keeping his distance, keeping the company of Gregor the Snail, Newter, Shamrock and Spitfire.  They looked a little the worse for wear, with burns, scrapes and bandages.  Had Tattletale pulled them away from a job?



``Hey, F,'' Tattletale said, smiling.



Faultline didn't return the smile.  ``You're aware that I'm going to track you down, beat you to a pulp and leave you tied up for the authorities to collect if we don't get our payment?''



``You'll get your payment the minute I have access to a computer Shatterbird hasn't toasted,'' Tattletale said.  ``No sweat.''



``I'm harboring serious doubts,'' Faultline said.  She glanced at Echidna, ``But I can look at this situation, and I understand if there's a rush here.  How does this work?''



``Really simple,'' Tattletale said.  ``We should get Labyrinth clear, though.  Then I'll show you.''



Faultline gave her a look, then hurried to Labyrinth's side, dodging a wall that was erupting from the ground to fit into the greater structure.  The ground surrounding the temple-like tower had changed, with an ornate inlay of what looked to be artificial flowers.  The petals were gold leaf, the stems the black-gray metal of iron.  The thorns, I couldn't help but notice, were real, like needles, sticking out of the ground.  Dangerous ground to tread.



As Faultline led Labyrinth to safety, I put one hand on Tattletale's shoulder to get her attention.  ``You sure?''



``I've got a theory.  With the clues on the passengers that we got not so long ago, about the powers, the idea of how the things work, I'm getting a sense of the bigger picture.  I think I could spend a decade working it out, but the basics of it?  I think there's a lot of powers that are a lot more versatile than their owners are aware, because they never get the opportunity to leverage it.''



Above us, Legend followed through on one cape's attacks, opening a wound in Noelle's side.  Grace leaped in as the laser stopped, grabbed a cape that had been exposed by Legend's attack, then kicked herself free, bringing the cape with her.



Another cape exhaled a cloud of what might have been acid vapor in Noelle's direction, apparently to slow the healing of the wound.  It didn't make much of a difference.



``Based on what?'' I asked Tattletale.



``It's all part of a whole,'' she replied, absently.  Her focus was on the others.  ``Scrub!  Get closer to the tower!  Everyone else, get back!  Labyrinth, don't use your power any more!  Hold off!''



Heads turned.  People had no doubt noticed the tower, but now something was happening.



Scrub stepped closer, and one of his explosions ripped through the air.  Another followed shortly after, intersecting one area of altered road.



Like a gas in the air that had been ignited, the entire thing went up in a heartbeat.  In an instant, it was a white void, as undefinable as Grue's darkness, perceivable by the edges, but with zero depth or dimension.  He'd shunted out the entire structure, as well as everything that had altered on the ground, but nothing had come back.



The door had been kicked out of the frame.



To look at it, I'd almost expected a rush of wind as the void on the other side sucked everything into it, like the vacuum of space.  There was only the sensation of a breeze as the air flowed into it.



Alexandria landed next to us, with enough force that I nearly lost my footing.  Every set of eyes that wasn't on Echidna was on \emph{us}, now.



``What did you do?''



``Made a hole,'' Tattletale said.



``\emph{Apparently}.  You didn't ask?  You didn't consider the ramifications of this?  Close it \emph{now}.''



``Who said we could close it?'' Tattletale asked.



``You're a \emph{fool},'' Alexandria said.  She set one hand around Tattletale's neck.  She could have killed Tattletale with a squeeze, but she didn't.  A \emph{threat}.



``I'd be careful,'' a cape growled, from the periphery of the scene.  I didn't recognize the man.  He wore a costume in orange with red metal claws.  Alexandria turned to look at him, and he added, ``Wasn't so long ago that your \emph{partner }called us \emph{all} fools.''



In the background, Echidna screeched.  She fought her way forward through the crowd, but the battle lines were holding, now.  Our side hadn't been surprised, this time, and the only capes in her reach were capes she couldn't absorb.  The rest were staying well back.



She wasn't an Endbringer, in the end.  It would be impossible to trap any of them like this, to get an advantage.  They had other tools, ways to exert pressure that were entirely independent of their own abilities.  Behemoth generated storms and background radiation, Leviathan had the waves, the Simurgh had her scream.



``That wasn't \emph{him},'' Alexandria said.  ``It wasn't \emph{Eidolon} who said that.''



``Close enough,'' the cape said.  ``Let her go.  You can't throw around authority you don't have.''



``As of this moment, I am still Chief Director of the PRT, and I am the leader of the Protectorate team that overlooks the second largest city in the United States.  That hasn't changed.  At the end of the day, I'll face any consequences I have to, but for now, I'm still in charge.''



``Your authority doesn't mean anything if they don't accept it,'' Tattletale said, staring Alexandria in the eyes.  ``Put me down.''



``I can't let this go any further.''



``In case you haven't noticed,'' Tattletale said, ``There's no further to go.  It's pretty much \emph{gone}.  All that's left is to find out whether this is a useful trick we just pulled or a \emph{really} useful trick.''



``Useful?''  Alexandria asked.



``Worst case scenario, it's a place we can dump Echidna.  A place where she won't be able to hurt anyone.''



``Or?''



``Or Labyrinth figures out that she can work with this.''



The hole blurred, colors consolidating into forms.  I could see Faultline standing by Labyrinth, arms folded.



``Labyrinth\ldots the shaker twelve,'' Alexandria said.



``That's the one,'' Tattletale said.  ``Mind letting go of my throat?''



Alexandria let go, but settled her hands on Tattletale's shoulders.  The implied threat was still there, just not so imminent.



``It's deep,'' Labyrinth said.  Her voice was faint, as if from far away.  ``There's so much there.  Worlds that I didn't make.''



``All parts of a whole,'' Tattletale mused.  ``Okay, Labyrinth.  The world we're looking for isn't very deep at all.  In fact, it's very, very close to the surface.  When you push into that world, it'll feel \emph{easier}.  Like a path that someone's already walked, more than once.''



``There's two like that.''



I would have missed it if it weren't for my bugs.  Alexandria reacted, stiffening, a slight straightening of her back.



Behind us, Echidna roared and threw herself against the barrier of ice and forcefields that surrounded her.



I turned toward Alexandria.  ``What?''



``I didn't say anything,'' she responded.  Her hands still rested on Tattletale's shoulders.



\emph{You didn't have to}, I thought.  But I wasn't sure how to use the information, and I didn't want to distract anyone from the subject at hand.



``Look,'' Labyrinth said.  ``One's like this\ldots''



The image shifted.  I wasn't the only one who walked around to get a better view through the window.  The landscape on the other side the window was different, the grassy hills that had been Brockton Bay before settlement, the distant beaches.  There were houses, but they were squat and blocky, half-overgrown.



Again, the slightest reaction from Alexandria.



``\ldotsAnd here's the other.''



Another landscape.  A city, like Brockton Bay, with different buildings.  Intact, undamaged.  It looked like a back road, one that didn't get much in the way of traffic.  Apparently the streets in \emph{that} Brockton Bay were in different places.



``Earth Aleph,'' Tattletale said.



\emph{The Travelers' world?}



``Are you \emph{insane}?'' Alexandria asked.  ``There's sanctions, treaties, \emph{truces}.  If you open this hole to Earth Aleph, it could mean a war between universes.''



``If that war was possible,'' Tattletale said, ``We'd have had it already.  The possibility of a whole other world of resources is too much to pass up.  Sure, our side has more raw firepower, by a factor of a hundred, but their side has just as many nukes.  It's a zero sum war.''



``You don't understand what you're getting into.''



``What I understand is that accidents happen, and everyone in earshot will call this particular interuniversal portal as an accident, because it keeps things peaceful.  I \emph{also} understand that this keeps Brockton Bay on the map.  Any other circumstance, people are going to keep trying to scrap this city, to accept that it's too costly to rebuild, that the criminal element holds too much power.  They'll throw bill after bill out there until the right combination of people are in power, the right hands can be greased, and Brockton Bay gets bulldozed and paved over.''



``It still could,'' a cape said.



``Oh, sure, \emph{theoretically,}'' Tattletale said.  ``But there's really two options here.  Either we spread the word, and a whole sub-industry explodes around this simple little doorway, accessing and trading information between worlds, research, a mess of other stuff, a city full of residents who've put up with disaster after disaster get work, get their homes rebuilt, and ultimately get their second chance.''



``Or we keep this a secret,'' I finished her thought, ``And we get none of that.''



``Or we keep this a secret,'' Tattletale agreed, ``We do what \emph{Alexandria} wants, and everything stays hush hush, just the way the big bad secret organization likes it.''



I could see the capes around us paying attention.  Ten, fifteen capes, from cities all across America and Canada.



``You have \emph{no}\emph{idea} what you're doing,'' Alexandria said.



``Fucking you over?''



``You're putting \emph{everything} at stake.  All of us, this world.  Even if we ignore the chance of our very first \emph{interdimensional} war-''



``Traitor!'' someone shouted from the sidelines, cutting her off.



Alexandria turned her head to try and identify the culprit.  I got the impression she wasn't used to people insulting her.  There were more capes nearby.  Miss Militia had backed up, but was keeping her eyes on the spot where Echidna was trapped.  On the far side of the clearing where the gateway stood, Gregor the Snail escorted a bound Sundancer and Ballistic to the periphery of the area.



``I can't help but agree with Alexandria,'' Faultline said.  ``This is reckless.''



``More than a little,'' Tattletale agreed.  ``But I'm not sure you heard the full story.  I only heard it secondhand, and I was with you from the time your helicopter arrived.  When we last ran into Newter, you guys were looking for dirt on Cauldron.  You still looking?''



Faultline's eyes narrowed.  ``Why?''



``No less than ten minutes ago, Eidolon's evil double admitted full culpability.  The Triumvirate, much of the upper levels of the Protectorate.  Kidnapping people from other universes, experimenting on them to figure out some power-inducing formulas, dropping them here.  Might help you to understand why people are giving Alexandria the evil eye.''



Faultline glanced at Alexandria.  ``A little too easy, to find out like this.''



``It's not the full story,'' Tattletale said, ``Not by half.  But it should inform your call on whether to side with her or not.''



Faultline frowned.  ``That's not\ldots no.  Maybe she is the person behind the scenes.  Fine.  But that doesn't change the fact that she might be \emph{right}.  Better to have Labyrinth find another universe to link to.  Maybe one where a mountain is blocking the other side of this gateway, if we can't close it.''



``Why do you have to be so \emph{reasonable}?'' Tattletale asked.  ``That's the worst of both worlds.''



``It's not \emph{war},'' Faultline retorted.



``Stop,'' Chevalier said.  People parted to give him room to enter the clearing.  ``There's other concerns.  The deal that was described to me was that the Travelers would do what they could to eliminate Echidna.  Failing that, we find a way to move her through the gap and deposit her in a place where she can do no harm.  That's our first priority.''



There was a murmur of agreement.



``Want to go home, Sundancer?  B-man?'' Tattletale asked.  ``Genesis?  Oliver?''



Ballistic, Genesis and Oliver stared at the opening.  Sundancer was shaking her head.



``What?''



Sundancer spoke, ``I\ldots it's not home anymore, is it?  I'm not \emph{me}.  Can't go back to the way things were.  I've killed people.  Accidentally, but I've \emph{killed}.  I have powers.  If I went there, I wouldn't be Marissa.  I'd be\ldots Sundancer.  I'd be famous.  If anyone found out about me, or if there was something in the media that goes between worlds, that clued them in\ldots''



``They don't have to know,'' Tattletale said.



``I don't\ldots I don't know if I can.''



I spoke up, ``Are you talking about going home, or killing Noelle?''



``She's\ldots she was my best friend.''



``She's not Noelle anymore,'' I said.



Sundancer shook her head.



``Go,'' Tattletale said.  ``She's not happy like this.  You do this, then you go home.  You give your mom a hug, fabricate an excuse to explain why you disappeared, and then go back to life as normal.  Never use your powers again, if you don't want to.  See if you can eventually convince yourself that none of this ever happened.''



``It's not that easy.''



``No.  But it's a hell of a lot better than staying here, isn't it?''  Tattletale asked.



``She's my \emph{friend}.''



``Was,'' I said.  ``It's a big difference.''



Sundancer looked at the mound of ice, rock and forcefields.  Echidna was thrusting her clawed hands through the barriers, only for them to be reinforced.



``Are there\ldots does she have anyone inside her?''



``There's-'' Tattletale started.  I flew a bug into her mouth and down her throat, and she choked.



``No,'' I lied.  ``I've been keeping track with my bugs.  Weld and the others got everyone out.''



\emph{Saved everyone they could.  }If Weld had backed out and nobody else was able to free the small handful that were still trapped, that was it.



Nobody was correcting me.  They \emph{knew}, but they weren't correcting me.



Sundancer hung her head.  She started approaching Echidna, her hands cupped in front of her.



``Move!''  Chevalier shouted.  ``Clear out of the way!''



Capes began to retreat.  Final patch-up jobs were thrown onto the mound of rock, forcefields and ice before the respective capes turned and ran.



It took Sundancer a long few seconds to form the miniature sun.  When it was formed, she held it over her head, letting it grow with every passing second.



I had to back away as the heat reached me.  I could note how the ice was melting, even though it was a hundred feet away.



Echidna roared and threw herself against her temporary prison.  Rock and melting ice tumbled away.  She began to claw free, until her upper body was exposed.  Capes opened with ranged fire, tearing into her forelimbs and limiting her mobility.  Alexandria dropped Tattletale and cast off her cape, before flying in and helping to hold Echidna in place.



``Marissa!''  Echidna screamed, her voice guttural, voiced from five different mouths.  ``Mars!  It's too soon!  I want to kill them!  I want to kill them all!  Kill this world!  Destroy this universe that did this to me!  Not yet, Mars!''



The sun flew forward, melting pavement as it traveled, before it enveloped Echidna, Alexandria and the prison of ice and stone.



It hung there for nearly a minute, deafening with its sizzling and crackling.



The sun flickered and went out. Echidna wasn't there any more.  Only sections of her feet were still in contact with the ground, bones and claws scorched black, crumbling and decaying like any part of her did when disconnected from the core that supplied her with power.



Alexandria was there in the midst of it, panting for breath.  Her costume had burned away, and only the metal pieces remained, including helmet, belt and metal underwear, each so hot they were melting and running over her skin.



But Sundancer was already turning away, not wanting to see it for herself.  She pulled off her mask and threw it aside.  Blond hair tumbled down around her shoulders, half-covering her downcast face.



Piece by piece, she removed her costume, not caring in the slightest about the watching crowd.  Each discarded piece sank into the melted ground around her or smoked on contact with it.  When she'd finished, she wore only her camisole and terry shorts.  The ground was still shiny and smoking from the sheer heat as she approached, left cool and solid in her wake.



She stepped into the portal, without a word, and then looked around, confused.  She took another few steps, and passed around the side of the portal as though it were merely a corner, out of sight.



The other Travelers went through next.  Oliver and Genesis didn't look like anything but ordinary people, with no costume or monstrous form, respectively.  They merely passed through.



Ballistic hesitated for long seconds.  ``Trickster?''



``We have him in custody.  He'll go to the Birdcage,'' Chevalier said.



``Good.  Because we don't want him,'' Ballistic said.



He walked through the portal, still wearing his costume.



``Can you close it?'' Faultline asked, when Ballistic had disappeared from sight.



``No.  Not really,'' Labyrinth said.  ``I can pick a different world.  So there's no war.  Or do like you said, find a place where a mountain covers the hole.''



``Feel free,'' Tattletale said, grinning.  ``In fact, that might even be \emph{more} useful.  Can you \emph{imagine} how significant Brockton Bay might become, if we had a whole unpopulated world to get to, harvest for resources, and Brockton Bay was the terminal you had to pass through?''



Faultline frowned.  ``You used us.''



``I \emph{hired} you.  Not my fault if you didn't ask for enough money.''



Faultline put her arm around Labyrinth's shoulders.  ``Can you find a world without people?''



``I\ldots yes.  There's one with lots of trees.  I'm looking all over, and I can't find anyone at all.  Not even on the other side of the oceans.  Only animals.''



``That'll do,'' Faultline said.  She looked at Tattletale, ``Not for you.  Only because I couldn't stand to let her be responsible for an Endbringer finding a defenseless world.''



``Much obliged, whatever the reasoning,'' Tattletale replied.  She flashed a smile.



Faultline only frowned and turned to usher Labyrinth away.



``Wait,'' someone called out.



Weld, with the red skinned boy and Gully beside him.  They caught up with Faultline's crew.



Whatever words they exchanged, I didn't get a chance to hear.  There was no way that the `monsters' could serve the Protectorate.  Faultline was a known element, someone who had, as far as everyone was aware, always been good to the people I was now thinking of as the Cauldron-made.



I couldn't even begin to guess where they'd go from there, but they'd have stuff to talk about, no doubt.



I'd mentioned to Tattletale that I'd felt adrift, after letting Dinah go.  Untethered, I think, was the word I'd used.  Everyone here now felt like that, to some degree.  The future had never been quite this uncertain.



I saw Alexandria standing by the sideline.  Eidolon had gathered her heavy cape where she'd tossed it aside and was helping to drape it around her shoulders.  I wasn't the only one looking, but she was oblivious, uncaring.  She still stood with all the confidence in the world.



She was barely covered, with one hand pinching the cape shut in front of her, traces of now-cooled metal lacing through her hair, the eyebrow and eyelashes of her one good eye.  It highlighted the lines at the corner of her eye, a finer metal finding its way into the crevices.  Her other eye held only a scarred over ruin with cooled metal pooled in the deeper recesses.  There were nubs of melted metal rods, no doubt there to help hold a high-end prosthetic in place.  Tinker-made, if she'd been hiding her injury to play the role of the PRT's Chief Director.



Without Echidna to divide our number, our ranks were free to line up in a rough semicircle around Alexandria and Eidolon.



``Nobody can know what happened today,'' Alexandria said, utterly calm.



Someone scoffed.  ``You want us to \emph{keep}\emph{your secret?}''



``Not the secret,'' she said, unfazed by the scoff.  ``Echidna.  Four capes were inside her when she was scoured away.  More were injured or killed in the course of the fight, or in Shatterbird's attack.  We can't cover that up.  We shouldn't.  They were good capes.  But we can't tell the whole story.''



``You don't get to say that,'' the ice-generating cape said.  ``You have no place, saying that.''



``I won't argue,'' Alexandria said.  ``Everything we did, we did for the right reasons.  I understand it's ugly, without the context.''



Someone at the front spat in her face.  Alexandria didn't even blink.  She let the spit run down around the ruined pit where her eye had been, much like she had with the molten metal.



``If word were to get out about the clones, the ramifications would be too damaging.  We've spent \emph{decades} cultivating an illusion, that we're heroes.  Decades shaking the idea that we're killing machines.  The nature of this fight threatens to reveal just how much damage even the more mundane of us parahumans could do to the common people.  That's not only the clones and what they\emph{ did, but how we} dealt with the clones, in turn.  We can't shatter the image that the Protectorate has so painstakingly built, or the entire world will turn on us.''



``And the \emph{Protectorate}?'' Miss Militia asked, her voice hard.



``What of it?''



``The involvement with Cauldron.  It won't stand, not like this.''



``It \emph{has} to,'' Alexandria replied.  ``Too much depends on the Protectorate, even internationally.  If it crumbles, then the whole world suffers for it.  Other teams around the world would go without the resources we provide.  If it means keeping the Protectorate intact, I will step down.  I'll tender my resignation as Chief Director of the PRT, effective the moment I can reach my desk.  I'll consent to being watched until the moment I can step down as Alexandria, if you are uncomfortable with me continuing to serve the Protectorate in costume.  Eidolon, I'm sure, will do the same.  Myrddin's death will be excuse enough for our retirements.''



``What about Legend?'' Miss Militia asked.



Alexandria raised her head, staring up at where Legend hung in the air, unmoving.



``He was only aware of the most basic elements.  That Cauldron sold powers, but not how we tested them.  He did not know of our relation to the Nine.''



``He made excuses for you,'' Miss Militia said.  ``Lied.  We can't trust him any more than we can trust you.''



``I'm aware.  But what he does next is ultimately up to him.  I am only telling you what I know, and I know he did not know as much as Eidolon and I did.''



``That's not good enough,'' a cape said.  ``You've committed crimes against humanity.  You bastards should be \emph{tried}.''



``Do that, and the whole world pays.  Every cape would come under scrutiny, both from other parahumans and from the public.  Teams would dissolve, faith would falter, and I sincerely doubt we'd last through the next two Endbringer attacks in that kind of a state.''



All around me, capes exchanged glances.  I could hear angry murmurs, my swarm could sense fists clenching in anger.



``And the captives?  The people from other worlds Cauldron kidnapped?''  Miss Militia asked.



``Anyone with clearance should know that the number of people with physical mutations has declined steeply.  We've stopped experimenting.''



``Or so you \emph{say},'' Tattletale cut in.



``I do.  Tell me I'm lying, Tattletale,'' Alexandria said.



Tattletale shook her head.



``You need us,'' Alexandria said.  ``If not for the assistance we can provide in the face of class-S threats, then for the image, for the \emph{idea}.  I'm trusting that each of you are sane enough, \emph{reasonable }enough, to understand that.  You could come after us, but I assure you it wouldn't be worth it.''



``And Cauldron?'' someone asked.



``As I said, we're only barely involved.  If you want to try going after them and get justice for what happened to the captives, feel free.  Just know that we can't help you there.  We can't give you access or information, because they're out of your reach, and in the wake of all \emph{this, }they'll be out of our reach too.''



I felt numb.  She was everything I despised.  Authority, the institution, the self-serving people in power, the \emph{untouchable}.  All around me, I could hear angry voices, each trying to drown the others out.  Chevalier was among them, Miss Militia was quiet.



\emph{Tattletale} was quiet, oddly enough.



``I-'' I started, but the voices drowned me out.



My swarm buzzed with noise.  People startled and jumped as the bugs moved, shifting from the various positions where I'd more or less hidden them at elbows and in armor plates.



I stepped out of the crowd, toward Alexandria, and then turned my back to her, facing the capes.  So many eyes on me.



``She's right,'' I said, my swarm carrying my voice for effect.



Voices rose in anger, and again, I had my swarm move, buzzing violently, until they stopped.



``I'm not a public speaker, so I'll make it short.  I've got a long history with the Protectorate, a hell of a lot more experience being angry with them.  I wouldn't be where I am if it weren't for them, and that's not a good thing, not entirely.  But Alexandria's right.  Not about Cauldron, or the human experimentation.  I don't know anything about that.  But she's right that we shouldn't make any rash descisions.  Talk it out with your teammates before you make a call.  Maybe the various team and squad leaders should convene, form a unanimous decision.  I don't know.  But\ldots don't let your anger push you to do something that affects everyone.  Please.''



A second passed.



``You're not with the PRT, are you?'' a cape asked.



``No,'' I said.



``So you don't have to wake up tomorrow and go to work, pretend like everything's normal?''



``No.''



``Work beside someone, wondering if they lied about their trigger event?  If they maybe got their powers from a \emph{bottle}, something made only because some \emph{psychopaths},'' he spat the word out at Alexandria, ``Decided to experiment on innocent people and sell the results at a profit?''



``No.  I don't really have to wonder about that.''



``Then where the \emph{fuck} do you get off, telling us what to do, then?''



``Calm down, Jouster,'' Miss Militia said.



``It's fine,'' I said.  ``You're right.  It's not my place,'' I said.  I looked at Miss Militia and Chevalier.  Clockblocker was just a little ways behind them.  ``Thanks for hearing me out.  Good luck.''



Atlas flew to my position.  I drew my bugs around me and took flight, rising well into the air and hiding myself in the mass of bugs before pausing to adjust to a sitting position.



I saw Legend hovering in the air.  His fists were clenched, and he was looking down.  He looked \emph{agonized}.



If I'd had any idea what to say, I might have approached him.  I didn't.



With a command, I directed Atlas away from the discussion that could decide history, maybe even the fate of the world.



\sectionbreak



I sat on the railing of my balcony, Atlas' body hidden behind the towel-covered railing, serving as a footrest while I fed him a much-needed meal.  Unfolded pieces of paper sat in each of my hands.



I couldn't stand to be there any longer.  I'd said what I could, for what little it was worth, but I was too tired, the stakes were too high, and Jouster had been right.  The consequences might have been world-spanning, but it was ultimately up to the Protectorate to decide what happened next.  I didn't like feeling that helpless.



Beneath me, some kids from my territory were carrying boxes of treats I'd ordered two days ago.  They'd take more than their fair share, but they'd distribute the treats to the other people in my territory, people who had likely gone a good little while without a chocolate bar or bag of chewy candy.



There hadn't been any clones in my range as I zig-zagged my way to the North end, no signs of swarm activity.  I'd stopped by home, checked things over with my bugs, and my dad was there, more or less fine.



I'd go home in just a little while.  It wasn't a peaceful place, though.  This was.  My territory, being with people I'd taken care of, people I'd protected and fought for.  My heart was easier here than it was around my dad.



I was aware of the approaching figure, twisted around to get a look at Lisa.



``Can I come up?''



I pointed at the door, followed her movements as she navigated her way past Charlotte and up the stairs.  She reached the balcony and stepped out to hop onto the end of the railing opposite me.



``I own the land the hole to the other universe is on,'' Tattletale said.  ``Or Coil's fake name does, and I can finagle that so I have control over it.''



I nodded.  ``The meeting?  Did they decide?''



``Legend left first.  Then Alexandria and Eidolon.  The heroes were still talking when I left.''



``Okay,'' I said.  That didn't mean anything, not exactly, but it was better than the alternative.  The longer they talked, the more tempers would cool.



Perversely, I almost hoped that Cauldron had the clout to silence a few angry voices.  I could only hope that they were few and far enough between that the story wouldn't reach the public.



``Rex,'' Tattletale said.



``Hm?''



``His name was Reggie, but he got into sports in high school.  They started calling him Rex, until everyone used the name.  I don't mean this to be insulting, but you were kind of opposites in a lot of ways.  He was this popular guy, \emph{charming}.''



``Your boyfriend?''



She laughed, a short sound.  ``My brother.''



``Oh.''



``My family was well-to-do, I think that's come up.''



``Yeah.''



``When you're that rich, when you have people working under you who do the chores and handle the stuff that you'd normally do with your family, sometimes it's hard to stay a family, you know?''



\emph{Not really}, I thought, but I nodded.



She gave me a funny look, but she didn't call me on it.  ``It gets to this point where, you know, your cool older brother only spends time with you because it's his duty as a sibling.  And when you realize that, it sort of hurts.  Makes it insulting.  I think I caught on to that around the time I started high school.  I stopped accepting those \emph{token} offers of siblinghood.  We were brother and sister, we lived in the same house, went to the same school.  Our paths crossed, but we didn't interact.  We were strangers.  He was caught up being the popular senior, and I kind of resented him for it.''



``For not being a brother?''



Lisa shrugged.  ``Don't know.  More for \emph{acting} like a brother than not being a real brother.  For being the popular kid, being the favorite child, heir to the family businesses.''



``What happened?''



``I started noticing, he was in rough shape.  The smiles seemed fake, he'd get angry easier.  Was bottling something up inside.''



``What was it?''



Lisa shrugged.  ``I've dwelled on it so long I've imagined possibilities and derailed my train of thought.  Even with my power, I can't guess.''



``And something happened?''



``He slowly got more and more distant.  He'd fake more smiles, get a little more angry, a little more reckless.  And then one day he offed himself.''



Just around the corner, some kids were screaming and shouting as they played.  One boy was pelting another with chocolate pellets.  The victim shrieked in pain.



My bugs swept over the boy with the chocolates, and the pair froze.  They looked around, trying and failing to see me, then ran for the nearest alleyway, fight forgotten.



``I'm sorry,'' I said.



``So am I,'' Lisa sighed.  ``I've spent so long trying to figure it out, but I couldn't.  You'd think the star athlete might be gay, but it wasn't that.  Something else.  I let on to my family that I'd noticed something, after, and they started blaming me.  They were grieving, but that doesn't excuse it, does it?''



I shook my head.



``Calling me stupid, an idiot,'' Lisa looked away.  ``It got to be too much, like I was in a pressure cooker, everywhere I went, it was about him, and there was always this feeling, like everyone was aware that I'd known something and hadn't spoken up, hadn't done something to help.  I think I had my trigger event while I was asleep, tossing and turning and dreaming about it all.  And then, boom, I wake up and I start figuring stuff out, with killer migraines on the side.  Maybe if I'd caught on that it was powers sooner, I might have been more secretive, but my dad caught on.  Did a complete turnaround.  Faked affection, hid the real feelings, all to get me to use my power for the family's benefit.''



Lisa shrugged.  ``I was already seeing too much ugly, even before the powers.  Seeing more of it?  Seeing when people were being fake, when everything else was still screwy because of Rex's suicide?  It was too much.  I took more money than I should have from my parents and I ran.''



``And Coil eventually found you.''



She nodded.  ``And I eventually found \emph{you}.  I took one look at you, and I had a grasp of what was going on.  Didn't take too long for me to notice that you had that same air around you that Rex did.  Maybe I did what I could to save you because I couldn't save him.''



``Earlier, you said that you couldn't talk to me about the problem because I \emph{was} the problem.''



``I saw it when you pulled the trigger, offed Coil.  You saved Dinah, and you described how you felt adrift in the aftermath of it.  But you found a new focus.  You could fight Echidna.  Save the city.  Me?  When you shot Coil, I realized I was done.  I'd helped you out of the same trap of despair Rex had been in.  Don't know if the road I helped you down was a good one or a bad, but I'd \emph{finished}.''



``But why be reckless?  Why take the risks?''



``Because I did what I had to do, I helped you, and I still feel like the stupid, self-obsessed little \emph{child} that let her big brother die.  It wasn't conscious, but maybe I felt like I needed to up the stakes.  Pull something dramatic.  Show that, with these crazy smart capes like Alexandria and Faultline around, I could still be the smartest person in the room.''



``And do you feel like the smartest person in the room?''  I asked.



She stared out over the cityscape.  ``Maybe- maybe when the interuniversal trade takes off.  Can you imagine?  With me and you as the top dogs?  The whole world will pay attention to us.''



I hopped down from the railing, walking around Atlas as I made my way to Lisa.  I wrapped my arms around her, and she returned the hug.



I crumpled the papers in my fists.





