





Rey hesitated at the door.  He cast a wary glance over his shoulder, but life elsewhere in the city continued as normal.



If he touched the doorknob, any number of things could happen.  A pit underfoot, a guillotine blade from overhead.



It took a measure of courage to raise the door knocker and slam it against the front door of the old Victorian-styled house.



The door opened right away.



``Blasto,'' Accord greeted him.  ``We finally meet.''



``Uh huh,'' Rey replied.  He glanced around.  The inside of the house was \emph{nice}.  \emph{Must be nice to not have to reinvest ninety percent of your earnings on tech.}



``No mask?''  Accord asked.



``Yes,''  Rey replied.  He folded one corner of his face back.  ``It's a fungus.  Same texture as human flesh.''



Accord's own intricate mechanical face shifted in response to his underlying expression.  ``Lovely.''



``I'm still not sure about this, given our history,'' Rey said.  He accepted the invitation into the front hallway of the house, carefully removed his shoes and set them on the tray to the right of the door.



``I've given you my word that you'll be safe, provided you cooperate.''



``Damn Nazis,'' Rey said.  ``My whole lab, gone.''



Accord didn't offer any sympathy.  ``Come.''



Rey followed.  Peering into the rooms he passed, he saw libraries and sitting rooms, old furniture.  Everything was finely made, nothing cheap or throwaway.  Knowing Accord, it was all too possible that the man had hand-crafted everything in this house.



And in each room were people in costume.  Other teams had themes, natural or otherwise.  Their costumes matched, or they unconsciously mirrored one another in style of dress or quality.  Accord's people were much the same, but it was very deliberate.  Each wore fine clothing, elegant dresses and suits, and each had their hair neatly combed into place, oiled to the point that it looked wet.  The `costumes' were in the color of their chosen formal wear and badges or brooches they wore, as well as the finely crafted masks that hid any trace of their real expressions.



``You're not expecting me to dress like them, are you?''



``No,'' Accord said.  ``Truth be told, I fear you could never meet my standards, and I'm going to do my level best to ignore the fact that you exist.  You'll want to keep to the areas I designate and use the back ways out of the building, so that I never see you.''



``You're not going to imprison me, are you?''



``No.  This is a business transaction.  I will give you the opportunity to get back on your feet, you will do what you can to eliminate our mutual enemies, being careful to avoid any damage or criminal activity within my territory, and in exchange, you will give me half your territory when all of this is over.  Following such an event, I hope we can avoid any further aggression between us for the future.''



``Sure,'' Rey said.



``The individuals in question are Menja, Stormtiger, Cricket, Rune, Othala, Niflheim and Muspelheim.  I'll see you have all available records.  Best to enter any confrontation with your eyes wide open.''



``Okay.''



``My people will not be available to you, understand.  Our bargain presumes you are working alone.''



``I get it.''



``You're quiet.  You don't have questions?  Requests?''



``Wouldn't mind some grass.''



``Turf?''



Rey smirked, ``In the slang sense.  I meant--''



``Say no more.  I understand what you meant.  Provided you stay out of my way, you can do whatever you wish in the assigned area.  That said, I and my people will not provide intoxicants, and if you are inebriated in any way in my company--''



``It's fine,'' Rey cut in.  ``I get it.''



``Here.  Into the basement,'' Accord said.



Accord led the way, and Rey hesitantly followed.



The basement was expansive.  There were no walls – only pillars.  The floor was concrete covered in a no-slip perforated rubber mat, the various desks were stainless steel, each on wheels that could be locked in place.  Each desk, in turn, had glass cabinets or drawers.  As far as Rey could see, they were fully stocked.



But it was more than that.  Rey was used to the usual labs, which held years of old material.  Tools that had long since fallen into disrepair.  Trays of solutions that nobody had touched in years, too old to use but too expensive to throw away in good conscience.  There were slides that were stained, tools that didn't always work.  Even when he'd started his lab, it had been with tools stolen from his old University, things bought on the cheap.



This?  This was a dream.  He stepped over to a glass case, large enough to fit a person inside.  There was a case attached to one side with room for a solution to be poured in, and what he took to be an attached tank of distilled water, with a control panel to select the rate and degree of mixture.  Another tube would vent the contents into a biohazard case.



A glance told him that everything would be here.  There were neatly ordered bins of chemicals, tools laid out in neat rows.  Everything was pristine.  The cages on the other end of the room with the captive animals, even, were clean, with none of the animal scent or vague smell of waste that accompanied such.  There were troughs filled with rich smelling earth, thoroughly mixed and free of clumps.



Rey Andino could create life from raw materials, fashion a homunculus from the most basic ingredients and elements.  He could make monsters, loyal beings that would do as he wished, with only time and things he'd picked up from a drug store.  Faced with this laboratory, he felt small, insignificant.  He knew he would soil it, that things would break as he used them.  It was \emph{wrong}.



``Satisfactory?'' Accord asked.



``It'll have to do,'' Rey replied, trying to sound casual.



``It will.  Now, I'd like you to know that I recently acquired some samples and records.  I'd intended to hold on to them as a bargaining chip at a critical moment, or something I might offer you as incentive to leave this city.''



``What are you talking about?''



``You'll find them in the far corner of the room.  The computer contains the database and the attached machine arm will withdraw any samples on request.''



``Sure,'' Rey said.



``My ambassadors will be taking turns observing you.  Short of a critical emergency, they won't be reporting anything to me.  Citrine will be first.''



Rey nodded.  He was already heading to the computers, to find what Accord would feel was so powerful or valuable that Rey would leave the city to get his hands on it.



The computer was fast.  Rey started to empty his pockets and smooth out the papers with the few blueprints he'd been able to salvage when the white supremacists had come storming through his old lab, and the computer was already idling at the desktop screen by the time he'd finished.



A black window with text in bold white letters showed a menu.  Two options:



A:  View Database
B:  View Samples



He took the first option, typing the letter in the keyboard and striking the enter key.



It was names.  Cape names.  They kept appearing, so fast he could barely read them, and the window kept scrolling until he hit the enter key again to interrupt it.



He scrolled up until he found one name.  He clicked it.



Blasto, Real Name Unknown
Classification:  Tinker 6 (sub: master 5, blaster 2, shifter 2, brute 2); plants.
Disposition: Villain (B)Last Known Location:  Boston (Allston area, east).



Crime lord of East Allston since est. date of April 2009.  No subordinates.  No past history as a subordinate.  Criminal history indicates cap of second degree murder, tendency to mass damage to property and persons.  Produces uncontrolled lifeforms that are incapable of replication.  Adversarial relationship with \emph{Accord (#13151), Spree (#14755) and Chain Man (#14114)}.



Note:  High risk of Class-S classification.  Should creations self-propagate, kill orders are pre-authorized.



A: More information/History
B: More information/Powers
C: More information/Contact & Network
D: Back



There were signs of degraded data, but it was there.  Accord had somehow acquired the PRT's system data and records on all parahumans they'd encountered.



No big surprises on the possible kill order.  He'd been made aware of it some time ago, and had grumbled, groaned and grudgingly avoided making any lifeforms that could breed in the years since.



``How the hell did you get this?'' he asked.  He turned around.



It wasn't Accord behind him.  It was a young woman in a formal, silk dress, yellow trimmed with gold, and a mask in matching colors.  A gemstone stood out on her forehead, with matching earrings dangling from her ears like chandeliers.  Her hands were clasped in front of her.



``I didn't,'' she said.



``You're one of his\ldots what did he call you?''



``His ambassadors.''



``That's right.  Do you have a name?''



``Citrine.''



``Ok.  How did he get this?''



``I can't tell you that.''



``Because you don't know or because you won't say?''



``Yes.''



He sighed, turning back to the system.  He selected the last option in the menu at the bottom of the page, then reloaded the master list, stopping when it had progressed far enough.



Eidolon.  There was a full set of details.



More information?  Nothing.  Data not found.



Powers?  Nothing.  Data not found.



Legend was the same.



Maybe someone less prominent.  He selected Chevalier and got the standard information.  More details.



Powers?  He selected the option, and received pages upon pages of testing data.  Rey's eyes pored over the results, soaking them in.  It was like reading Shakespeare.  One could listen to a line, and be momentarily baffled, but skimming it or assuming a general foundation of knowledge, it was possible to pick up the gist of the message;  The underlying meanings, if not the exact definitions of the individual elements.



The work of a tinker wasn't typical science.  Refining it was science, but the blunt, raw use of the power?  It was almost the opposite.



Good science meant starting with the conditions, forming a hypothesis, making a prediction, and then testing it.  Repeat, repeat, repeat, until there was a solid base of knowledge.  That knowledge let one establish further conditions, refine hypotheses.



But tinkers started with the end result.  A moment of inspiration, glimpses of the major steps one would need to take to get there.  It involved working \emph{backwards}, up until that moment the means came into view.  Rey could see it at work, could see Chevalier's power as raw data, something he could replicate by traveling an entirely different path.  He would need a sturdier frame.  Something big.  This wouldn't be a hybrid of a stray dog and a plant.  This would need to be something closer to a bear.



Or, he realized, a human.



He backed out of Chevalier's data until he was at the original screen.  He checked the samples Accord had provided him with.



Select sub-database:
A)  PRT (Protectorate, Wards) samples
B) Non-PRT (evidence database) samples
C) Misc samples



Further investigation revealed the full truth.  Accord had gotten his hands on a database of DNA from countless members of the Protectorate and the Wards, as well as scraps of material from certain powers, where traces remained behind.



He selected C, expecting little.  His eyes widened.



Many were samples from lifeforms that various tinkers and masters had created.  His own were in there.  That wasn't the surprising fact.



He selected the last option on the list.  To the right of the computer, in a hermetically sealed case, a robotic arm extended and deposited a microscopic sample on a slide.



A fragment, so small as to be nearly impossible to see, of one of the Simurgh's feathers.



``You keep making these little oohs and ahhs,'' Citrine commented.  ``It sounds like you're pleasuring yourself.''



``I am, believe me,'' Rey replied, not looking her way.  ``Where did he get this stuff?  Does he even comprehend what he gave me?''



``I'm sure he does.''



He'd considered replicating Chevalier's power, with a solid enough frame.  Maybe a bear, maybe a human.  Small potatoes.



He went through the contents he'd unloaded from his pockets until he found a piece of paper he'd folded into an envelope.  He tore it open and tapped out the contents.



Each seed was about the size of a pea, tapered at each end, a mottled white-brown.  He hurried over to one of the large glass tubes and fiddled with the controls until it started flooding with water.



``Are you one of the talkative ones?'' Citrine asked.



``What?''



``I mean, maybe it's a dumb question, because you've stuck pretty much to monosyllabic grunts since this whole thing started, but I'm wondering if you're one of the capes that likes to rant or one of the quiet ones.''



``Quiet.  Why?''



``Honestly?  I'm bored.  Not like I can go on Facebook with my smartphone or anything.  That sort of thing gets you killed, when you work for Accord.''



``You want me to \emph{entertain} you?''



``I doubt you're capable.  But you \emph{could} distract me, help while away the minutes.''



He eyed the woman.  Rey wasn't one of the quiet ones by \emph{choice}.  He'd just fallen into the habit of being alone because it was easier to stay in the lab than it was to be out in the larger world.  People in the larger world \emph{sucked}.  Up until the Nazis from Brockton Bay had  turned up and claimed the building at the other end of the street from his lab, it had been a place he could retreat.  A place where his work and his art could occupy his thoughts and distract him from reality.



Art.  It was a good starting point for an explanation, and she was probably the most attractive person he'd spent more than one minute around in the last few months\ldots



He forced a smile.  He was a little rusty on that front.  ``What we do, what tinkers do, it's more art than science.  Every step we take is made with an end goal in mind.  Just now, looking over these samples, I think I decided on an end goal.''



``What's that?''



``My usual methods, well, you know them.  You've fought my creations before.''



``Yes.''



``These seeds,'' he raised one hand, a seed pinched between index finger and thumb, ``Are like stem cells.  They harbor the potential to become virtually anything.  Wherever information is missing, they fill in the gaps.''



``Like using frog DNA for dinosaurs.''



``Like using frog DNA for dinosaurs, right.  The way I worked it, they'll decode the information in a very brute force way.  The seed starts by forming two bodies, attached by a central hub.  I kill the least viable one, it buds and splits again, with copies that are derivatives of the survivor.  Usually two to four.  Kill all but one, repeat.''



``Until you have something viable.''



``Exactly!  Takes anywhere from a few hours to a few days.  Then I have what's essentially a plant-animal hybrid, and I nudge it in the direction of my enemies.  Or give it simple programming that I can use.  Training half-plant rodents to fetch shiny objects, for example.''



``How?''



``Trade secret,'' Rey said.  ``I'm not dumb.  I won't give away the essentials.''



``Okay.  So what's today's project?''



``Oh, I'll have a \emph{dozen} projects in the work before I let myself go to sleep.  But the big one is that I want to replicate an Endbringer.''



He glanced at Citrine, saw that she'd gone still.



``I may need to go talk to Accord,'' she said.



``No need,'' Rey said.  ``I suspect he already knows.  He \emph{gave} me these samples, no doubt with the idea that I'd use it.''



``And you can't even control it?  Or \emph{he} can't control it?  It doesn't sound like him,'' Citrine said.



Rey paused.  It \emph{didn't} sound like Accord.  Was there another explanation?



Accord might be planning on killing him after the project was done.  Rey kept his creations in line with pheromones, spraying them liberally around his lab and the surrounding neighborhood.  They would move to the nearest unaffected location as soon as they were free.  Once he did that to Accord's home, the place would be rendered immune to his own attacks, at least for a little while.



But it still seemed too reckless for the perfectionist.  Was Accord that eager to kill the white supremacists?  Or was there another plan in the works?



``You've gone quiet,'' Citrine said.



``Thinking,'' he said.  ``No, I need things quiet for a minute.  There's a TV in the corner.  Watch that.''



``I can't.  Accord would be upset,'' the woman in yellow replied.



Rey sighed.  He crossed the room to the television, turned it on, set it to mute and turned on the closed captions.  ``He won't be upset if \emph{I} turn it on, will he?''



``No.''



``There.''



He returned to the computer and started working with the Simurgh's tissue.  It was hard to cut, and harder still to slice to the point that he could look at it under a microscope.



``Crystalline,'' he murmured, as he focused on it.  The feathers were like snowflakes when viewed at 40x magnification.  He scaled all the way up to 800x magnification before realizing that there were no individual cells.



Was it just the feather?  Was it dead tissue, on par with the keratin of fingernails or hair?  He used the computer to access a sample of Leviathan's `blood', and let the hands handle the arrangement of preparing the slide.  Being liquid, the blood was easier than the feather.



He wasn't sure he wanted to use Leviathan's tissue.  Growing a miniature Leviathan in a vat would be a bad idea if that vat was filled with fluid.



Using Behemoth's tissues would be just as problematic.  The Herokiller could ignore the Manton effect at a range of up to thirty-two feet.  Even semi-conscious inside a glass case, it was too risky.



Had to be smart about this.



Leviathan's blood was the same as the feather.  Crystals, dense and so opaque that light wouldn't pass through them.



There were more tissues.  Flesh.  More blood.  Hair.  Damaged tissues and intact ones.  He went through each.



All of it, the same.  Crystals.  No individual cells.  Even the crystals barely differentiated from one another.  Truth was, there was more difference in crystals collected from deeper inside the Endbringer than there was in crystals that had come from different parts of the Endbringer's body; hair as opposed to blood.



He scraped off a bit of his seed, then added water and the catalysts to splice it with some of the Simurgh's feather.  Sure enough, it started to grow.  Each end of the scraping formed into buds, and the buds started to form into basic, foetal shapes, one quadruped, one vaguely humanoid.



But neither \emph{lived}.



The weaker tissue was easier to work with.  Assuming it was deriving patterns from the crystals, insofar as the crystals could create or support life, he could use that to work out the peculiarities of how the Endbringers were able to sustain themselves.



No vascular system, no sign of emergent organs.



Of course the emerging lifeform wasn't viable.  It wasn't capable of life in the first place.



He'd have to take another route.  He withdrew a sample of Myrddin's tissue, then started splicing it with one seed and the ruined fragments of the Simurgh's feather.



It was lunacy, tampering with Endbringer-related materials, but he couldn't shake the idea that he was on to something.  He'd sustain the Endbringer tissues with other living tissue that could feed it energy or nutrients.  His seeds would bridge the gap.  It would take ten or fifteen minutes before he saw any real results.  There was other work to do in the meantime.



A sedated monkey plus a sample of his own tissue and one seed, and he had a homunculus in the works.  It would be roughly as intelligent as a very stupid person in most respects, but it would share his own understanding of chemistry, biology, science and botany.  It would serve as a lab assistant, and he would need one for a lab this big.



The rest of the seeds went into another vat to replicate.  He'd need more.



He walked over to the glass tube where the Simurgh-Myrddin-plant hybrid was in the works.  One had wings rather than legs.  He directed a laser to kill it.  The other had four arms, but two resembled wings.  It would work.  He conducted a charge through the fluid to reset the life cycle.  It would split in two or three, and he'd kill the remainder.



Accord must have based this equipment off of the stuff he'd had in his \emph{last} lab, the one Accord had forcibly ejected him from.  The lasers being built into the glass tube were a nice touch, kept everything hermetically sealed.



In a fit of whimsy, he directed the lasers to a pure light form, then had them fire into the glass case itself.  Letters lit up, labeling the projects.  Regrowth for the plant that was growing and budding with more seeds.  Homunculus for the monkey that was gestating in the second tube.



And for his \emph{real }project?  It would have to be something fitting.



Morr\'{i}gan.



Beautiful.  He studied the three foetal forms that were developing inside, killed two, narrowing down the results he wanted.  Like pruning branches.



The TV started making noise.  Rey wheeled around to see Citrine and one of her fellow `ambassadors' standing in front of the TV.  The man in the suit with a green dress shirt and a copper lizard mask was the one turning up the volume.



``I'm trying to \emph{work} here,'' Rey said.



``Something's going on.  Look,'' the man spoke.



Rey impatiently left his work behind.  If he waited too long, a bad growth could be carried on to the young.  Wouldn't do.



The TV showed a reporter talking.  Why was he supposed to care?



Then it changed to a camera view of an ongoing conflict.  Three gigantic armored suits were in open conflict with a small group of people.



The Slaughterhouse Nine.  \emph{Here}, in Boston.



One of the suits was deploying swarms of drones, but they were getting cut out of the air as fast as they appeared.  Another member of the Nine had a loose-fitting coat of human flesh draped over him.  He stretched it out to grab surrounding buildings and anchor himself in place as a mechanical lizard with a giant wheel on its back tried to haul him in with what looked to be an immense suction.



The Siberian had made contact with and was tearing apart a third suit.



A suit high in the air fired off a laser beam, and the Siberian jumped to put herself in the line of fire.



Whatever happened next, the camera didn't catch it.  The concussive force of the laser hitting was enough to knock the cameraman over, and the image shorted out.



Rey sniffed.  He'd like to see more of Dragon's work, not because it had anything in common with his own, but because it was \emph{good} work.  But for now, his focus was on his projects.



With a quick glance, he assessed and executed two homunculus-offshoots and one derivative of the Morr\'{i}gan.  Electrical charges restarted the gestation process.



The thing was starting to resemble the Simurgh, though both feathers and hair were brown-black in color, it was hermaphroditic and the flesh was more translucent than white.  Veins stood out.



Rey studied it while the thing cracked in the middle, the individual halves separating with a thread of flesh between them.  Each of the halves began dissolving and forming anew.



If it was even half as powerful as the real Simurgh\ldots well, this would be a game-changer.



And Accord had to know that.  Had to be aware that Rey would be working with the Endbringer tissues on this level.



It wasn't as though the method of control was that difficult to master.  One set of pheromones would make the creation feel fond of something, the other would have an negative effect, drive them away from a person or area.  Still another would provoke feelings of anger or hatred, useful if he wanted to bid them to attack.



If Accord found the pheromones, he could be rid of Rey, and he'd have whatever creations Rey had put together in the meantime.



It would be at least a day before the Morr\'{i}gan was fully grown.  He had that long to think of an answer.



The door slammed shut.  Citrine had gone upstairs.  The lizard-masked man watched the television.



Time passed, and he watched the results with interest. The Morr\'{i}gan was now forming with two arms, two legs, and vestigal wings.  He let it develop to the point that it was roughly two months old, then killed the offshoots.  He started running x-ray scans and doing biopsies, picking through the results to fine tune the internal changes and monitor how much of the lifeform was Simurgh, versus being Myrddin or plant-based.  He was judicious and merciless in executing the offshoots, keeping them from growing to a point where there was even a \emph{chance} of them being sentient.



The lifeform did, he noted with some pleasure, have a Corona Pollentia; a lobe in the brain that would allow for powers if it developed fully.



While the man watched the unfolding news, Rey took the opportunity to brew and spray himself with a set of pheromones.  His creations would be more favorably inclined towards him now.



The door at the top of the stairs closed.  He turned to see that the lizard-man was being relieved.  Had that much time passed already?



``You being good?'' the woman asked.  She wore a black evening gown with a slit all the way up to her hip.  It would have been alluring, but her mask was black, with black lenses and spikes radiating from the edges.  Her brooch was of a black star.



``Making headway,'' Rey responded.



``One of your fucked up creations broke my leg last year.  \emph{Please} give me an excuse to hurt you.  Please.''



``I'll pass,'' Rey said, turning his attention to the homunculus.  He calibrated the signal, pressing two electrodes to his own forehead, then sent the readings out to his creation.



When it was done, he drained the fluid and vented the chamber.  The glass sank into the floor, and the homunculus crawled out, using its knuckles to walk.  Its skin was peeling, more like loose bark crossed with scar tissue than flesh.  



``You retain any English?''  He asked.



The homunculus nodded.



``Spanish?''



Another nod.



``Go dispose of the slides.  Consider everything a top priority biohazard.''



The homunculus found a pair of rubber gloves and began cleaning up the mess from the early experiments.



Rey studied the Morr\'{i}gan.  Alarms were set to go off if it approached one month of age.  With Myrddin's brain tissues and the current state of growth in Simurgh-derived parts, there was little to no chance that it would achieve any degree of self awareness.



A glance out the window that overlooked the street showed that it was getting dark.  He'd been here all day.



The door slammed at the top of the stairs.  He sighed in irritation.  Time was passing too quickly.  Would \emph{this} one threaten his life too?



There was a crash, and he nearly jumped out of his skin.  He wheeled around.



The woman with the black dress had slammed into the television set.  She had holes in her as though she were a piece of Swiss cheese, and more of her had been torn to shreds.



A body fell down the stairs.  The man with the lizard mask.  Dead, though not so mutilated.



The woman who came down the stairs had an unusual body type accented by her style of dress.  She was almost like a boy, she was so thin, and her strapless dress hugged her upper body, but the lower half billowed around her.  Her hair was long and white, her eyes wide with irises and pupils small.  Her lips had been painted black.



Her arms though\ldots machinery had been crammed into the arms, and they'd been extended to nearly twice the length, the fingers drawn out long.  Sparks flew as the woman moved one arm, and she winced.



The second individual skipped down the stairs, stopping at the bottom to admire the laboratory.



Her eyes fell on Rey.



``I know you!'' she said.



``I know you too, Bonesaw,'' he said.  Without breaking eye contact, he tapped a key on the computer, prompting a flood of nutrients into the Morr\'{i}gan's solution.



``Nice lab.''



``It's not mine.''



``Man, it's\ldots this is nice stuff.  Being constantly on the move, you miss out on stuff like this.''



``My old lab wasn't this good,'' he said.  \emph{Make small talk}.  ``Who's that?''



``Damsel of Distress, with some modifications by yours truly.  Damsel for short.  Better at controlling her power now.''



``Hi Damsel.''



Damsel looked at him, spoke in a whisper he couldn't make out.



``And who's \emph{this}?'' Bonesaw asked.  She approached the glass case with the Morr\'{i}gan inside.



``Morr\'{i}gan.''



``Looks like the Simurgh.''



``She is.  In part.  The other half of the genetic base is from Myrddin's tissue.  Everything that bridges the gap is a really complex fungus.''



``Cripes.  How do you even manage something like that?''



``Trade secret,'' he said.  He watched as Damsel approached the widescreen TV, picked it up where it had fallen to the ground, and held it in front of her, staring at the image, no doubt some mention of what the other members of the Slaughterhouse Nine were up to in Boston.



``I'll get the answer out of you, you know.''



``I know,'' Rey admitted.  ``But I wouldn't be a self-respecting tinker if I didn't at least \emph{pretend} to protect my work.''



``True.''



Bonesaw turned her attention to the homunculus.  She poked it in the stomach and it growled at her in response.



If he let the Morr\'{i}gan out now\ldots Bonesaw was staring at the homunculus, and Damsel was focused on the TV\ldots



But it would die if he let it go now.  It was too young.  Every two or three seconds it sat in the high-nutrient solution would be a week of growth.  He'd need it at least at four or five years of age before it was capable of moving and acting, and he'd still be depending on it having powers rather than a defunct corona pollentia.



He'd never experienced a stronger emotion than he did when he saw another set of feet appear at the top of the stairs.  They made their way down, and each step brought more of the figure into view.  If it was another member of the Slaughterhouse Nine, he'd die.  If it was one of Accord's ambassadors\ldots



He'd probably still die.  But there'd be a chance.



It was neither.



The man reached the bottom of the stairs, turned his head to survey the scene.  He wore a visor that combined the movable visor of a knight's helm with a high-tech equivalent, and the points where they met his helmet were shaped like a lizard's frill or a dragon's wing.  He held out a rod in one hand, and it unfolded into a spear of ridiculous length.



The lizard theme\ldots if the machines Rey had seen fighting the Slaughterhouse Nine were Dragon's, was this one of her assistants?  Someone working under her?



Or \emph{her}?



Damsel wheeled around, extended one hand, but the man in armor was quick to step around a pillar for cover.  Damsel's power ripped into the pillar, warping and tearing space in a chaotic storm.



The man in armor ducked and rolled to reach the next piece of cover, one of the stainless steel desks.  He arrested his momentum with one outstretched arm, then kicked the desk with both feet.  It slammed into Damsel.



He hopped onto his feet in a single movement, slashing with the spear's point.  The tip struck Damsel across the eyes, blinding her.  He reversed the spear and swung it, and the spear-butt caught her in the side of the head.  She was knocked down onto all fours before she could direct her power at him again.



The man dug the spear's point into the ground to help propel himself towards her.  His leg flared with a gray blur as he reached her, and be brought it down onto her back from above.



It sheared through her as though she weren't even there, cutting her in half.  He kicked out to obliterate her head and one of her shoulders in a single movement, disabled the gray blur, and set his foot down with a thud that rang through the underground laboratory.



Bonesaw didn't seem disturbed by the loss of her teammate.  ``Don't think I don't recognize \emph{you}.  You were Mannequin's pick.  Armsman?  Armsmaster?''



The man in armor pointed his spear at her.  ``Defiant now.''



``You know I loaded myself with a mess of epidemics, Defiant,'' Bonesaw said.  ``You kill me like that and I'll explode into a cloud of a bajillion plagues.  It can't be \emph{easy}.''



``It is,'' Defiant's voice was distorted by his helmet, vaguely computerized.  There was a processor at work somewhere there, Rey observed.



``What, you'll unleash a thousand plagues on this world to finish me off?  Me?  A little girl?''  Bonesaw smiled wide.



``Yes.''



``You'll get sick.''



``Biohazard safe,'' Defiant said.  His spear shaft tapped against his armor.



``\emph{He'll} die in a hundred horrible ways,'' Bonesaw said, pointing at Rey.



``Villain.  Acceptable loss.''



``And the people in this neighborhood?''



``I scanned the area.  There is zero air flow in or out of this lab.  It's quarantine-safe.''



``So you've got all this figured out, don't you?''



``Yes.''



Bonesaw glanced over her shoulder at Rey, ``You--''



Defiant moved so fast that Rey couldn't follow the movement.  The spear impaled the girl in the chest.  The heart.



``Ugh, fuck me,'' Bonesaw grunted.



Defiant swung the spear to one side and slammed her into the wall, knocking chemicals and vials off of every shelf unit she hit on the way.



``Why--'' Bonesaw started.



Defiant raised the spear and her sentence was interrupted as her head cracked against the ceiling.  He drove the spear toward the ground with just as much force.



``Why\ldots'' Bonesaw spat blood onto the ground.  Being impaled in the heart hadn't put her down.  ``Ow.  Bit my tongue.  Why don't you come closer, big man?  Too scared to come here and finish me off?''



Defiant didn't respond.  Instead, he struck her against the wall again, then shoved the spear point into a set of stainless steel shelves.  Pieces of the empty glass beakers rained onto the ground beneath her dangling feet.



``Coward!'' she taunted him.



Rey glanced nervously toward the door.  Would it be better to run or to stay?



The girl reached forward, clutching the shaft of the spear.  She began pulling herself forward, hauling the spear's shaft through the hole in her chest as she closed the distance inches at a time.



She smiled as she did it.



Blades sprung from the length of the shaft, and began spinning like propellers   One caught her from behind, and she slid forward, only to find herself sandwiched between two such sets.



``That's Mannequin's trick!  That's so cute, that you're copying--''



Defiant moved the spear, and Bonesaw was thrown back, her hair and back caught against the blades.  She used her hands to pull herself forward so she was clear, maintaining a grip even as he swept the spear to one side again, keeping herself fixed at the same point on the pole's length.



``Hey, plant geek!'' Bonesaw had to raise her voice to be heard, ``He kills me, you die!  Think about that!''



Rey glanced at Defiant.  There wasn't an opening or anything that suggested at the man inside.  Only armor, implacable, unrelenting, driven.



Then he looked at the girl, half-hidden behind the blur of the spinning blades.



``Okay,'' Rey said.



He wanted to live.  Wanted nothing more than to go on to do his research, maybe one day find greatness, find a woman who could appreciate him.  Have kids.



But he wanted \emph{her} to live even less than he wanted any of that.  Because he could well and truly believe that she would do more harm in her life than any good he could do in his.



``Okay,'' he repeated.  \emph{I can live with that}.



There was a crunching sound, and Defiant snapped his head over to look at Bonesaw.



She spat, and smoke billowed where the spit came in contact with the blades.



One flew off and sailed across the room to strike a cage with animals inside.  The mechanism that was keeping the blades in motion ceased.



With nothing impeding her line of sight to Defiant, Bonesaw \emph{crunched} again.  Smoke billowed from her mouth as acid ate away at her flesh, she leaned back as if she were preparing to spit a loogie-



And Defiant disabled the propeller behind her, swinging the weapon and flinging her free of the end.



She touched ground and spat out a mouthful of acid onto the floor.  It smoked on contact with the concrete.



``No,'' Defiant said.  He took two steps forward and swiped with the spear, cutting her in half.



\emph{Almost} in half.  Something like chainmail was wrapped around her spine, but the spear had cut through the matching mesh that had protected her abdominal organs.



Defiant turned to catch a mechanical spider that was making its way down the stairs.  He impaled it and dashed it to pieces.  Another thrust killed one that was hiding inside an air vent.



Bonesaw crawled forward, dragging her spine and ruined midsection apart from her legs.  There wasn't as much blood as there should have been.  ``Not\ldots done.''



She clawed into her apron for vials, threw them across the room.  Defiant backed away as they exploded into clouds of white.  As they spread, Defiant was reduced to a mere silhouette.



\emph{You're in an augmented biohazard suit}, Rey thought.  He eyed Bonesaw as she clawed her way in his general direction.  \emph{Come through!}



But Defiant had other ideas.  Maybe he had a degree of familiarity with the white powder, knew what it was and that it had to be avoided.



Maybe there was something else at play.  Another member of the Slaughterhouse Nine in the area?



Bonesaw was getting closer.  Rey backed away.



She looked up at him.  Dark circles were already spreading around her eyes, her face paling.  She looked gaunt.  And she held a vial.  She tried to claw the cork off and failed.



If he stepped closer, she'd do something to him, but if he didn't try to stop her-



On the second try, the cork came free.  She pushed it in Rey's direction, and he was quick to kick it into the cloud of white to his right.



But the fluid that had trailed out as it rolled was smoking, just under his feet.  He had nowhere to go.



He lunged, leaping onto one of the shelving units to keep from passing anywhere near Bonesaw.



Something snagged on his foot.  He toppled to the ground.



Looking back, he could see her spine was prehensile, and that it had caught his foot, winding around the bridge of it.  \emph{The sheath is hiding more machinery}.



The white smoke was congealing into strands of gunk that cut off the end of the room closest to the stairwell.  Defiant was caught in the midst of it, and was slowly tearing himself free.



\emph{No.  No.}



Rey tried to kick her off, but that only served to let her get a grip on his other foot.  She began clawing her way up his legs.



He reached for the keyboard, pulled it down from the shelf it sat on.  It dangled above his head, and he pressed it against the wall, tapped the keys to open the tube that held the Morr\'{i}gan.



He hadn't drained the water, and the fluid began to flow onto the ground as the glass sank into the floor.



Bonesaw had climbed up to his chest, and it was only his struggles that kept her from reaching any higher.  He clawed at her hands, and she wasn't that \emph{strong}, but she was tenacious, and she used her prehensile spine to secure any progress she made.



Three limbs against his two.  He tried to stand, failed.  Too much weight in the wrong places, and he couldn't use his hands.



The water finished pouring out, and the Morr\'{i}gan took its first steps.  Five or six years old in apparent age, a vague replica of the Simurgh.  It would have some blend of her powers and Myrddin's.



Too busy looking at his creation, he was caught off guard as Bonesaw got hold of his throat with one hand.  She hauled herself up until her entire upper body was resting on his chest.  The sheath that had been around her spine pressed up against his face as the bone and attached machinery passed into his open mouth and down his throat.  His throat was scraped raw by the edges of it.



He choked, fought for breath, found none.



The Morr\'{i}gan flopped to the ground.  Dead.  Dumb.  Not viable.



Just as the crystalline feather and Leviathan's blood had been, it wasn't capable of sustaining life.  A failed experiment.



Needles punched their way out of Bonesaw's spine, found his own.  In one instant, he lost all sensation below his neck.



In the next, she was making him move, pulling him to his feet.  His head craned toward the ceiling, mouth forced open, blood trickling onto his face as the full weight of her upper body came to rest on his head.



``\emph{Just} got a fresh pair of hands, and \emph{this} happens,'' she muttered.  ``Do you know how long it's going to take to find and transplant a good pair of legs?''



She bid his hands to move as though they were her own.  At her will, he typed on the computer.  At her bidding, he turned his body to give her a better look at Defiant's progress, threw another vial at the man.



Back to the computer.



``Samples.  Evidence,'' Bonesaw murmured.  He could feel the vibrations of her voice against his face.  The air that was flowing from a tube by her spine and into his lungs was stagnant and foul, but she bid him to breathe and he breathed.



``Crawler,'' she said.  There was a whir.  She used his hand to shatter the glass case that held the samples, and he groaned in pain as the shards cut it.  She made him grab the sample from the robotic claw's grip.  ``Mannequin.''



She gathered the samples in her own hands while she used his hands to type and select the options.



``Burnscar, Shatterbird\ldots surprising how much DNA we've left on crime scenes.  Winter\ldots Chuckles\ldots''



Defiant roared.  He growled words, as if speaking to himself.



``Nice Guy, Murder Rat, Hatchet Face.  We've gone through a lot of members,'' she said, while depositing each sample in a plastic case.  ``Screamer, Harbinger, King.''



Rey choked, \emph{tried} to choke.  He could control his head, his mouth.  If he passed out, would his body fail?  Would \emph{she} fail?



``Pity I can't use this lab,'' Bonesaw said.  ``Make the cloning process that much easier.  But I've seen your work.  I think I can replicate it.  Helps if I have this\ldots''



She had him tap a key, and he could hear the water flowing as another of the glass cases started to move.  The Regrowth tube.  The seeds.



``Didn't think we'd get \emph{this} lucky,'' she said.  ``Jack said that since the world isn't ending like it was supposed to, he wants to hurry it along.  We did our research, and decided to track down some decent tinkers, and you were closest.  Only problem with entering any metropolis like this is security cameras\ldots Oooh!  Gray Boy!  He was one of Jack's first teammates!  You wouldn't believe the stories Jack tells about him.''



Another sample was collected and deposited in the box.



She stopped, and turned toward the Morr\'{i}gan.  He could feel his blood run cold.



``Nah,'' Bonesaw said.  ``Even I'm not \emph{that} crazy.''



She had him tap keys on the keyboard, and a laser fired from the top of the case that had held the Morr\'{i}gan.  He couldn't see, but he could smell the burning flesh.



The box of samples tucked under one arm, she walked Rey to the door that led out of the back of the basement.  The one Rey had been ordered to use when coming and going, out of Accord's sight.



He couldn't lose hope.  Defiant would have come on an armored suit.  If that suit was positioned to survey the area, if Defiant had contacted Dragon, ordered an airstrike or even just reinforcements-



No.  There was a ladder on the other side of the doorway, leading down into a pitch darkness.



She turned in Defiant's direction, and Rey caught a glimpse of the hero.  He was still caught, and though the blur around his leg was cutting him free, goop was streaming down from the ceiling to connect to his upper body, and he couldn't destroy that with a ready kick.



She had Rey grip the rungs of the ladder, and they slid down into the pitch black.



\sectionbreak



``I failed,'' Defiant said.



``You hurt her.  If anyone failed, it was me,'' Dragon replied.  ``I couldn't break away from the fight.''



Mist emanated from her robotic body, dissolving the strings of slime that had congealed around him.  Her hand settled on the side of his face.



``Did we gain \emph{anything}?''



``I'll show you in a minute.  Are you okay?''



``Need more tech.  Nanomolecular thorns for my arms.  It would have made the difference.''



``We can figure something out.  But are you okay?''



``I suppose so.  Where do we stand?''



``Two suits destroyed.  And we don't yet know what Bonesaw took with her.  Jack escaped with some of his team.  But we killed four of them, all together.''



``Four,'' he said.  ``We should mobilize now.  There's a limit to how fast and how far they can move, especially with the wounded.  Bonesaw went into the subway system, and it will take time for her to get free, but if she gets in contact with their new teleporter-``



``We'll mobilize as soon as I've freed you, Colin.  If I don't use this body, you'll be left behind, and neither of us want that.''



``Better that you give chase.''



``We're doing \emph{okay}.  We're closing the gap.  They showed up on camera, and we were ready to move on them within \emph{minutes}.  We'll do it again.''



Colin nodded, but he didn't respond.



She settled her arms around his shoulders, letting the spray do its work.  The metal of her forehead touched his mask.  ``Take it for what it is.  A little lost, a lot gained.''



It took thirty more seconds for the foam to dissolve.  She broke the hug and he tore himself free of the scraps.  They were out of the basement and walking through the ruined interior of Accord's household in moments.



They stepped outside into the evening air.  Colin let the vents in his costume open so the cool air could flow through.  Dragon luxuriated in the feel of the air against her exterior body.



Her hand caught his as they walked to where the Uther and her own suit were waiting.



Colin stopped in his tracks.  Dragon's suit was posed with its head pointing toward the sky.  The suit's metal jaws were clamped around a body.



Manton.



``The Siberian is dead?''



``\emph{Gone} would be a more appropriate word,'' she said.  ``\emph{Manton} is dead.''



Colin nodded and exhaled slowly.  ``Good work.''



``The job's not over yet.''



The Uther's cabin doors opened to invite him in.





