





Welcome to the Parahumans Online message boards.You are currently logged in, \underline{XxVoid CowboyxX}
You are viewing:
$\cdot$  Threads you have replied to
$\cdot$  AND Threads that have new replies
$\cdot$  OR private message conversations with new replies
$\cdot$  Thread OP is displayed.
$\cdot$  Ten posts per page
$\cdot$  Last ten messages in private message history.
$\cdot$  Threads and private messages are ordered chronologically.
You have six infractions and two warnings.  You were last banned on September 03, 2010.  Your probationary status expires in 63 days, on September 07, 2011.



\sectionbreak



\blacklozenge  Topic:  What the Fuck Happened?
In:  Boards \blacktriangleright News \blacktriangleright Events \blacktrianglerightAmerica
Bagrat (Original Poster) (Veteran Member) (The Guy in the Know)
Posted on June 22nd, 2011:



I admit it.  I'm a cape geek.  You know it.  I know it.  I'm the cape geek the OTHER cape geeks go to for the crusty, juicy details on what's happening and where.  Look at my badges^.  I'm the guy in the know, and everyone on the News boards knows me.



Except I'm not in the know.  I've been calling in every contact I know, some CAPES, even.  I've been watching four different news channels and scouring the internet, and I'm CLUELESS.



Someone clue me in?  I'm desperate.  What the hell happened in Brockton Bay?



EDIT:  Board rules say I'm supposed to contribute something if I'm starting a thread, so here's what I do know.  Someone help fill in the blanks:



$\cdot$  June 18th:  Mayor Christner of Brockton Bay flies to Washington.  Makes argument against evacuation.  Surprises more than a few people.  At the same time, multiple Dragon suits are reported in the city.



$\cdot$  June 19th:  Explosion at Brockton Bay town hall, after supervillain Coil attempts coup and tinker equipment misfires in the ensuing skirmish.  Christner and Director Emily Piggot hospitalized and sent to ICU.  Thirty or more people reported dead, including Coil and subordinates \"{U}ber, Leet and Circus, and a number of field reporters.



$\cdot$  June 20th:  Massive deployment to Brockton Bay.  Unspecified class A threat.  Cape wives on the boards confirm: something's up.
Two hours later:  Threat level upgraded to class S.  All Protectorate capes who subscribed to the emergency response measure and accompanying pay increase now forced to get over to Brockton Bay and help.  Legend and Alexandria are among them.
We have a \underline{\strong{report}} (see link) from White Fairy, one of three more notable board members on the ground in Brockton Bay, who says they started establishing quarantine procedures around the site of the battle.



Cape wives on the boards report calls from their husbands and wives saying they're ok by about noon.  A few casualties, Myrddin among them.  No report on what happened and who the cape was on the opposing side.



$\cdot$  June 21st:  Almost a day later, capes start filtering home.  Still no reports.
Brocktonite03 (second of the three excellent people on the ground that are giving us reports) travels all the way out of town to get his hands on a working computer.  Reports Shatterbird attack and apparent quarantine procedures in the middle of an empty lot downtown.  White tent and beginning construction around it.



And then nothing.  Help me out!



\strong{(Showing page 242 of 243)}



\blacktriangleright  \strong{Ekul}(Brockton Bay Refugee)
Replied on July 6th, 2011:
The theory makes sense.  Huge clean up involving a hundred plus bodies, portal to another world, it would be something that they'd want to keep from the public, and you could even call it Class S if that world had capes of its own.  Which they'd have to, if they wanted to kill Myrddin.  Were we at war with another Earth on June 20th?



\blacktriangleright \strong{AverageAlexandros }(Cape husband)
Replied on July 6th, 2011:
Does that fit the Class S scenario?  If nobody can answer I can ask my wife if she'll let me look through her regulations handbook.



\blacktriangleright\strong{ Lolitup}
Replied on July 6th, 2011:
Class S includs situations where threat can produce more threats which can produce more etc.  In scenario with a whole alt world of capes on par with our own they could have powers like that.  Sitch got upgraded to S after the first showed up?
(Posted from phone, sry)



\strong{\blacktriangleright XxVoid_CowboyxX} (At Ground Zero: Brockton Bay)
Replied on July 6th, 2011:
Scary [censored].  Imagine if they had their own Endbriners or Alexandria.



\blacktriangleright RobbyReplied on July 6th, 2011:
Two things:
1)  You don't need to censor yourself.
2)  Doesn't fit with what we know of alternate Earths. Breakdown of Haywire's research says we can't get to alt. Earths that are too close to our own.  Closest Earth to our own is Aleph, and deviation from that world started 30 years ago, the moment Scion arrived.  Anyone over 30 was born in both worlds, anyone under 30 wasn't, or the odds are almost impossible (same sperm, same egg, same time of conception required to have the same kid, and that's ignoring all the environmental influences during the pregnancy, and everything post-pregnancy that shapes the personality.)



\blacktriangleright TheGnatReplied on July 6th, 2011:
But Alexandria is over 30, isn't she?  It's not impossible they'd have a version of her.



\blacktriangleright RobbyReplied on July 6th, 2011:
With powers?  Improbable.
I doubt this alternate world we're talking about is exactly as far away as Earth Aleph, anyways.  I'd assume the point of deviation occurred more than thirty years ago, which lowers the chances even more.
In brief:  I doubt we have to worry about Endbringers and an evil Triumvirate.  This isn't the movies, and evil alternates are so overdone.



\strong{\blacktriangleright XxVoid_CowboyxX} (At Ground Zero: Brockton Bay)
Replied on July 6th, 2011:
I censored myself because I don't want an infraction and a ban for swearing.



\blacktriangleright\strong{ Chrome}
Replied on July 6th, 2011:
@ Void Cowboy: they don't give out infractions for swearing.
@ Everyone else:  I get that it makes sense on a lot of levels, but nothing's confirmed.  Any other theories?



\blacktriangleright TRJReplied on July 6th, 2011:
I'm going to get called a tinfoil hat, but what about that thing where the guy was talking about posts with the word C*auldron getting screened if they weren't censored?



End of Page.   \underline{1}, \underline{2}, \underline{3}, \underline{4}, \underline{5} \ldots \underline{241}, 242, \underline{243}



\sectionbreak



\strong{\blacklozenge  Private message from GstringGirl:}



\strong{GstringGirl: } i started to play it. i'm not good with the controls.\strong{XxVoid_CowboyxX:} Takes practice.  You gotta at least play through the individual template packages.  that lets you unlock the skills and takes the skill cap off for the individual traits.  Then you can build your own class and play in the Hero League with me.  I can show you the ropes and help you figure it out.\strong{GstringGirl: } i have it figured out.  i read the forums and watch videos.  i understand all that stuff. its the controls i struggle with.\strong{XxVoid_CowboyxX: } Practice, practice practice!\strong{GstringGirl: } i have a 33 percent win rate.  makes it so slow to unlock everything.  i liked that other game more.\strong{XxVoid_CowboyxX: } Don't even mention that game to me.  I'm still mad about it.\strong{GstringGirl:}\strong{ }sry. and i have to go now.  my parents want me off the computer. sister wants a turn.\strong{XxVoid_CowboyxX:}   Sorry I didn't reply.  Was in game.  Guess you already went to bed.  Listen, I'll be traveling this summer with my family.  Could swing your way, if you wanted to meet up.  Grab coffee?\strong{GstringGirl *New Message*:  }Oh.  Wow.  My parents are really strict, so I don't think I'll be able to.\strong{GstringGirl *New Message*:  }You haven't replied, so I sent you a text.  I can't receive texts back, so PM me, plz.



\sectionbreak



\blacklozenge  Topic:  The Ground Zero Badge
In:  Boards \blacktriangleright Places \blacktriangleright America \blacktrianglerightBrockton Bay \blacktrianglerightGround Zero (Private Board)
White Fairy (Veteran Member) (At Ground Zero: Brockton Bay)
Posted on June 31st, 2011:



I'm getting kind of fed up with this.  I talked about it with Alathea and Judge (the two original Brockton Bay board moderators) and Bagrat (major guy in the news section).  We got special dispensation to issue Brockton Bay Refugee and Ground Zero badges.  The goals were:
$\cdot$  It automatically give more weight to those of us who know more about what's going on in Brockton Bay, either because of our familiarity with the local capes or because we're \underline{there}.
$\cdot$  It's a way to get aid to people in trouble.  This was essential early on.  Someone's low on food or needs medical attention, the fact that they have a badge and that the badge is (presumably) validated means we can take a cry for help as something serious rather than a hoax.  (And for the record, I don't think a temporary ban is enough for the scumbags who faked cries for help – in the early days, traveling across the city to deliver supplies was \underline{life threatening})
$\cdot$  It furthers the interests of Parahumans Online, to disseminate information and allow network among people in the right positions.  The badges let people know who can be contacted for more information or people we can coordinate with for certain tasks.  Case in point: Bagrat contacts Brocktonite03 about the incident a week and a half ago, Brocktonite03 goes and finds the quarantine tent and construction.  I can then contact Brocktonite03 and we organize a way to take turns visiting the construction site and then report progress to the boards, with picture progress so you guys can speculate or offer your own expertise.
$\cdot$  Filters access for getting onto the private board, so people in the prior two situations can manage



But there's \underline{certain} individuals who aren't using the system as it's meant to be used.  People got the badges with the loose verification system that existed in the early stages (and the mess of new moderators that came on board to manage the board), and they're using them for status or to put incorrect information or outright lies out there.  Alathea and Judge said they're willing to do a ban from this sub-board (and all related boards) if details can't be confirmed with further validation.  I'm talking to moderators of the main boards about maybe banning them from the site altogether.



So we're proposing further validation\ldots
$\cdot$  A photo of yourself at any construction in progress or recent piece of paperwork (flier, shelter pamphlet, whatever), with the date and your username prominently displayed.  Doesn't have to show your face, a photo of a hand with the details written on it, with the quarantine building in the background is perfect.
$\cdot$  I will \underline{meet} you.  Time and place of your choosing, though I'd prefer to meet you halfway if you're a ways away from the Towers, and I won't go into any of the danger zones.  If you need supplies, I have access to batteries, supply kits, gas and a car, and I will deliver it to you when we meet.  I might have luxury goods, but you'll have to pay for those.



There's a limited time window here, because the city's slowly coming together, and people are moving back in.
Edit:  Now that people are moving back in, we'll start banning people who weren't able to verify.  If you contact us and can explain why you weren't able to verify, that's ok (stay in hospital, no connection/power where you were at).  We'd like to meet you in person or see where you were staying for verification that you were in the city during the time of crisis.



We're going down the list.  The unconfirmed will be banned when verification stops being possible.



Confirmed:
$\cdot$  Chilldrizzle – Met in person.  Delivered some fresh water and dog food.
$\cdot$  Morgan Sinister – Met in person.  Brought chocolate, chocolate was paid for.
$\cdot$  Lo A Quest – Met in person.  Talked for a few minutes, parted ways.
$\cdot$  Char – Met in person.  Had the best meal I've had in weeks on the Boardwalk.
$\cdot$  bothad – Photo verification
$\cdot$  Laser Augment – Photo verification



Banned:
$\cdot$  Aku-42 – Attempted to photoshop verification using an image Brocktonite03 already uploaded.
$\cdot$  Whackograve – Admitted lie.



I know this sounds ridiculous, but we use systems like this for a reason.  It can mean life or death, even.



\strong{(Showing page 4 of 4)}



\blacktriangleright  \strong{White Fairy} (Original Poster) (Veteran Member) (At Ground Zero: Brockton Bay)
Replied on July 6th, 2011:
@Void_Cowboy: you're \underline{exactly} the type I was talking about.  Where do I even begin?
Your posting hours on the site suggest you've got something occupying your time from early in the day to evening.  Like maybe school?  Except there's no school in Brockton Bay yet (soon).  You state your location as the north end of Brockton Bay, profess to have a generator and satellite internet.  Ok, not unheard of.  Except you've apparently got enoguh gas stockpiled to keep the generator going 24/7 and, oh yeah, you're in \underline{Bitch's} territory!  Bitch would maim or kill you for being in her territory, let alone making the kind of racket a generator does.



\blacktriangleright \strong{XxVoid_CowboyxX }(At Ground Zero: Brockton Bay)
Replied on July 6th, 2011:
I have a quality generator that doesn't make much noise.



\blacktriangleright \strong{Laser Augment }(At Ground Zero: Brockton Bay)
Replied on July 6th, 2011:
But no phone or camera to take a picture of yourself in the city?



\blacktriangleright \strong{XxVoid_CowboyxX }(At Ground Zero: Brockton Bay)
Replied on July 6th, 2011:
I have a camera, but I don't feel comfortable leaving the house.  That's the sort of thing that gets me killed by mutant dogs.



\blacktriangleright \strong{Laser Augment} (At Ground Zero: Brockton Bay)
Replied on July 6th, 2011:
You do know that Bitch left the north end a while ago?  How would you even miss the fact that you haven't heard howling in the last while?  If you're not leaving the house, why don't you take a picture of yourself by this high end generator of yours?  Because it doesn't exist.
You fuckers make me sick, like you can pretend to be all cool by being one of the survivors, who stuck it out through the Endbringer attack, the Nine and the gang wars.  But you left.  Your mommy and daddy took you out of town, and you're pretending you stuck it out, that you're here when you're not, all for a stupid internet badge and a peek at the private board.



End of Page.   \underline{1}, \underline{2}, \underline{3}, 4



\sectionbreak



\blacklozenge  Topic:  Legend Leaves the Protectorate
In:  Boards \blacktriangleright Teams \blacktriangleright Protectorate\strong{Brilliger} (Original Poster) (Moderator: Protectorate Main)
Posted on June 26th:



Word's out, and we're waiting for the Protectorate to give a statement before we get further details.  Legend is stepping down, citing family reasons.  He's already on record saying that he intends to offer his aid in crisis events, but will no longer be leading the Protectorate.  His successor has not yet been named.



\strong{(Showing page 1173 of 1180)}



\strong{\blacktriangleright XxVoid_CowboyxX} (At Ground Zero: Brockton Bay)
Replied on July 6th:
@ Lainerb
It should totally be Eidolon.



\blacktriangleright \strong{Valkyr} (Wiki Warrior)
Replied on July 6th, 2011:
@ Lainerb
They haven't picked a successor yet because it's a little more complicated than picking the strongest hero.  They need someone who works on a number of levels, as a leader (both in terms of day to day paperwork and management and in the field), an ambassador (there's no less than 30 teams around the world that work with the Protectorate to some degree), a powerhouse (can't be weak or you won't be respected) and from a marketing standpoint.



\blacktriangleright Coyote-CReplied on July 6th, 2011:
@ Cowboy
Can't be Eidolon.  He's strong, but he's not a leader.  There's a ton of references to people meeting him at conventions or cape wives meeting him at functions.  I won't say he's an asshole, though some have said he rubbed them the wrong way, but people definitely don't walk away from meeting him with that universal ``Oh my god he's so nice!'' reaction that they have with Legend.



\blacktriangleright \strong{Mock Moniker}
Replied on July 6th, 2011:
Not to mention that there's rumors Alexandria or Eidolon might step down.  There's a lot of animosity being directed at them from certain groups.  Look at \strong{this} link and \strong{this} one.  The monsters in the Protectorate have almost all left.  Only one who stayed, I think, are Hunch and Polish.  I've been thinking it's another Bastion incident.  Someone higher-up says something racist or offensive, the Protectorate pulls strings to try and cover it up, but offended people are still offended.  Run off to make their own team.



\blacktriangleright ChromeReplied on July 6th, 2011:
I don't know whether to be sad about it or not.  Weld's awesome, and it's great he gets to run his own team, but I was hoping he'd become a big figure in the Protectorate.  Why be a big fish in a small pond when you could be a big fish in a big pond?



\blacktriangleright NodReplied on July 6th, 2011:We don't know how big the Irregulars are going to get.



\strong{\blacktriangleright  Chrome}
Replied on July 6th, 2011:
But they're never going to be the Protectorate big.



\blacktriangleright \strong{Weld} (Verified Cape) (Irregulars)
Replied on July 6th, 2011:
I dunno, I'm optimistic. \winky
For the record, I harbor no animosity toward the Protectorate.  We're still attached, and we're receiving equipment, funding and contacts through them.  They were very respectful as a whole, but we got a chance to interact a few weeks ago, and we collectively agreed that while the Protectorate's plan to build a rapport between us Case-53s (as the Protectorate terms us) and the public was sound (making me leader of the Brockton Bay Wards, for example), it was too slow, and we could do more as a group.



\blacktriangleright \strong{Answer Key}
Replied on July 6th, 2011:
@ Weld:
I have questions:
1 – How much did they pay you guys to keep quiet and play nice?
2 – I notice you said you don't have issues with the protectorate `as a whole'.  You're not denying there's issues with one or two prominent members?
3 – What the hell happened on the 20th?
4 – How is making you leader of the wards in Brockton Bay a good thing?
@ everyone else:
Question – just wondering.  Who's been leading the Protectorate since Legend left?



\strong{\blacktriangleright  Whitecollar }(Cape Wife)
Replied on July 6th, 2011:
@ Answer Key – Tinfoil hats ahoy.  I can answer that last question, though.  Or my hubby can.  He says the Protectorate is currently being run by a joint team atm.  Chevalier, Alexandria and Prism are each handling different tasks.



\strong{End of Page.   1, 2, 3, 4, 5 \ldots 1172, 1173, 1174 \ldots 1180}



\sectionbreak



\blacklozenge  Topic:  The Endbringers, Thread XXXIV
In:  Boards \blacktriangleright World News \blacktriangleright Main
Lasersmile (Original Poster)
Posted on June 28th, 2011:



Starting a new topic because the last one hit post limit.
The Simurgh attacked Canberra, Australia on February 24th, 2011.  Thread \underline{\strong{here}}.
The Leviathan attacked Brockton Bay, America on May 15th, 2011.  Thread \underline{\strong{here}}.
Estimated time for next attack is August 30th, 2011.  This time is not exact, and is likely to deviate by as much as 15 days.
Official speculation points to Eastern Europe as the next likely target.



\strong{(Showing page 23 of 25)}



\blacktriangleright  \strong{Miss Mercury }(Protectorate Employee)
Replied on July 5th, 2011:
Speaking for someone in the thick of it all, I don't think that there's any expectation or assumption that recent events (losing Legend, losing Myrddin, several members leaving) will change the outcome of the next attack.  The Protectorate and immediately related teams only make up 25-50% of the defending side when outside of North America, and North America isn't a likely target.  There's been no policy changes or anything of the sort in the Protectorate that point to that degree of pessmism
-\Mercury



\blacktriangleright  Space ZombieReplied on July 5th, 2011:
I'm more inclined to think the PRT is making a mistake than to think they're on the ball.



My money's on a big-ass clusterfuck.  This is the first time since Behemoth first showed that we haven't had all our ducks in a row.  May's Leviathan attack had the lowest casualty rate we've ever had, but I think the next one's going to hurt us bad.



\blacktriangleright  \strong{Chaosfaith }
Replied on July 6th, 2011:
My cousins are traveling through Europe this year.  All the analysts say the odds are worse there.  Should I try convincing them to delay the trip to Greece?



I think I'm even spooked about there being an attack where I'm at (London, UK).  If I wanted to visit somewhere during the crisis point, would anyone have any recommendations?



\blacktriangleright  \strong{XxVoid_CowboyxX} (At Ground Zero: Brockton Bay)
Replied on July 6th, 2011:\texttt{O_o}  Definitely tell them to skip Greece.  I've seen an attack for myself and its worse than you think it would be.



I don't know where you could run to be safe, though.  Alaska?



\blacktriangleright  \strong{SenorEel}
Replied on July 6th, 2011:
Can't let the Endbringers dictate your life.  Live it as you can, know where the nearest shelter is, and keep a well stocked supply closet.



\blacktriangleright  \strong{ArchmageEin}
Replied on July 6th, 2011:
If you wanted to go anywhere, and I agree with SeniorEel that you shouldn't go just because you're scared, apparently Brockton Bay is putting itself back together.  The Endbringers never attack the same place twice in a row, so it's oddly the safest place to be, and it might help you to see the city for yourself.  The stories are/were bad, and scary stuff happened, but they made it.  They're still there.  You might find that reassuring?



\blacktriangleright  \strong{Tumbles}
Replied on July 6th, 2011:
That's if you don't mind being in a city where supervillains run the scene.



\blacktriangleright \strong{Xyloloup} (Brockton Bay Refugee)Replied on July 6th, 2011:
Copy pasting from one of my posts in another thread.  Current state of the villains in Brockton Bay:
$\cdot$  Skitter – Boardwalk/North end.  Five stars, almost no crime, free food, work if you want it.  Water and power both.  Heard from a friend that stayed there for a while that he ran into some trouble, his place got raided, stuff taken.  Mentioned it to someone in passing, and the next day it's all returned, with some cash (two hundred dollars) and a note apologizing for the trouble, assuring him the matter was dealt with.  He left after that, which I don't get (free money).  Said he was creeped out.
$\cdot$  Parian – Not a villain, but apparently struck a deal for a slice of territory at the very upper end of the city.  Not great, not bad.  Good spot to stay if you want a clear conscience and don't mind that the water and power aren't always on (80% of the time?) and shelters are a bit crowded.  Four and a half stars.
$\cdot$  Grue – Western end of the city, from the docks to the lake downtown.  Almost a nonentity, but he's apparently dealt with some people who tried to set up shop.  Pick where you stay carefully, cuz there's areas with power and water, areas without, and it doesn't change much day to day.  Three stars.
$\cdot$  Imp – Southernmost end of the city.  Shopping district, some of downtown.  There's a few dregs trying to set up shop with the no-name villain calling it her territory, and a few fights as a result (doesn't help that the big guns like Skitter are further away.)  I'd stay away from here because of that alone.
$\cdot$  Regent – Eastern end of downtown.  Kind of a shantytown, area got hit hardest by the waves, shelter water and power nearly nonexistent, but the places that you can get are nice and very expensive.  Some violence bleeding over from Imp's territory.  Nothing here unless you're rich and want to live like a king among serfs.



\blacktriangleright \strong{Procto the Unfortunate Tinker} (Not a tinker)
Replied on July 6th, 2011:
And Tattletale?  Bitch?



\blacktriangleright \strong{Sothoth}
Replied on July 6th, 2011:
Sorry to continue derailing thread, but Bitch apparently has a slice of the more remote areas, where you don't find many people living.  Captain's hill, the woods/hills, the beaches at the south that haven't been cleaned up yet.  Her gang's growing though, \underline{\strong{or so I hear}}.  Tattletale's not a fighter so it makes sense that she's more a behind the scenes person than one of the local warlords.  I think what Xylopop was saying was that the town's not so dangerous.  Probably more peaceful than it was at the start of the year, if you stay out of the very southernmost areas (and maybe the north – I heard there's a few upstarts from New York and Boston trying to get a foothold there in Parian's area) and turn around if you hear a lot of barking.



End of Page.   \underline{1}, \underline{2}, \underline{3}, \underline{4}, \underline{5} \ldots \underline{23}, 24, \underline{25}



\sectionbreak



\blacklozenge  Topic:  Hypothetically, if I wanted to become a henchman\ldots\strong{In:  Boards \blacktriangleright }\strong{Places \blacktriangleright America \blacktrianglerightBrockton Bay }\blacktriangleright Teams \blacktriangleright Undersiders
WagTheDog (Original Poster) (Brockton Bay Refugee)
Posted on July 1st, 2011:



Been a fan of Bitch/Hellhound/Rachel Lindt since the start.  Always loved dogs.  Always loved badasses.



She's both, and now she's one of the villains running the city?  So coooool!  If I wanted to become a henchman/henchwoman/henchperson (hypothetically) how would I do it?\strong{(Showing page 1 of 1)}



\blacktriangleright  \strong{Char}(At Ground Zero: Brockton Bay)
Replied on July 1st, 2011:
Sent you a private message.



\blacktriangleright  \strong{Good Ship Morpheus}
Replied on July 2nd, 2011:
Yeah, I might be too late to say anything, but I wanted to warn you to be careful.  Really, the reality could be different from the ideal you've built up in your head.



\blacktriangleright  \strong{WagTheDog }(Original Poster)
Replied on July 3rd, 2011:
Omg.
It's all good.
Harder than I thought but all good.



\blacktriangleright \strong{XxVoid_CowboyxX}
Replied on July 6th, 2011:
I came through a link on the main board.  Is this real life?  Can't you get arrested or banned doing something like this?



\blacktriangleright \strong{Laotsunn} (Kyushu Survivor)
Replied on July 7th, 2011:
Better arrested or banned than dead.  I'd say death is the thing to worry about here.



\blacktriangleright \strong{WagTheDog }(Original Poster)
Replied on July 7th, 2011:
All good, my man.  All good.



\strong{End of Page.  1}



\sectionbreak



\blacklozenge  Private Messages\strong{ from GstringGirl:}



(Two new messages not included, click \underline{here} to see)
GstringGirl *New Message*:  my phone broke so i'm messaging you here. you have to understand its not what you think.\strong{GstringGirl *New Message*:}  i just wanted to hang out and play space opera. \underline{you} were the one who approached \underline{me} so don't jump straight to the conclusion that I'm a ``middle aged pervert trying to get into your pants''.\strong{GstringGirl}\strong{*New Message*}:  theres a reason i cant send a photo but i don't want to have to explain,.,  cant we just go back to the way things were?\strong{GstringGirl *New Message*: }\frowny



\sectionbreak



\blacklozenge  Topic:  Who'd you lose?
In:  Boards \blacktriangleright Places \blacktriangleright America \blacktrianglerightBrockton Bay Discussion (Public Board)
Brocktonite03 (Original Poster) (Veteran Member) (At Ground Zero: Brockton Bay)
Posted on May 29th, 2011:



See topic.  Friends?  Family?
On topic posts only, please.  No commentary.  Nc= no condolences via. private message.



\strong{(Showing page 17 of 17)}



\blacktriangleright \strong{Mac's Dual}\strong{Rocket Propelled Grenades} (Brockton Bay Refugee)
Replied on July 6th:
Nobody close to me died, but I still did lose quite a few people.  My best friend moved away.  My other friend joined the Merchants because an artificial high was better than being lucid and uncertain.  Come to think of it, he might have died in that massacre at the Towers.  My parents were separated, but they still lived in the same city before.  My mom wants to move back, but my dad's gone to Florida and I don't know how much I'll see him.
Nc.\strong{ }



\blacktriangleright  \strong{Reave} (Verified PRT Agent) (Brockton Bay Refugee)
Replied on July 6th:
My coworker and squad captain.  Went to school together, dropped out together, joined the PRT as grunt forces.  S9 got him, and as glad as I am he died fast, given what might have happened, doesn't change the fact that he's gone.  Loved him more than I love my wife, in a way.
Nc.



\blacktriangleright  \strong{XxVoid_CowboyxX }(At Ground Zero: Brockton Bay)
Replied on July 6th:
My aunt and uncle.  They were attacked by Chosen, dragged out of their homes and beaten.  My uncle fought back and smashed this one guy in the nose, and wrestled a gun from his hand, but got punched in the throat and dropped the gun.  He fought back some more, but eventually got knocked to the ground and shot.  I wasn't there, but I heard he went down like a hero.



\blacktriangleright  \strong{White Fairy }(Veteran Member)\strong{ }(At Ground Zero: Brockton bay)
Replied on July 6th:
My boyfriend.  He was in a shelter Leviathan attacked.  Only about half of us made it.  One of the heroes bailed us out.  Distracted the Endbringer and led him away.  Nc.
@Void_Cowboy: How do you know the story if you weren't there?



\blacktriangleright \strong{XxVoid_CowboyxX }(At Ground Zero: Brockton Bay)
Replied on July 6th:
Leave me alone!\strong{User received an infraction for this post: all posts must be related to the topic question.}



\blacktriangleright \strong{Vista} (Verified Cape) (Wards ENE)
Replied on July 7th:
Gallant.  Aegis.  Battery.  Armsmaster.  Dauntless.  Velocity.  Glory Girl.  Browbeat.  One family member. I can't say who for obv. reasons.
Nc plz.



End of Page.   \underline{1}, \underline{2}, \underline{3}, \underline{4}, \underline{5} \ldots \underline{16}, 17



\sectionbreak



\blacklozenge  Topic:  Skitter\strong{ In:  Boards \blacktriangleright }\strong{Places \blacktriangleright America \blacktrianglerightBrockton Bay Discussion (Public Board)}\strong{Miraclemic} (Original Poster) (Brockton Bay Refugee)
Posted on June 11th, 2011:



The reason arachnophobes don't want to live in Brockton Bay.  Her discussion thread.



\strong{(Showing page 30 of 30)}



\blacktriangleright\strong{  }\strong{Mr. Fabuu} (Brockton Bay Refugee)
Replied on July 7th, 2011:
I'm not saying she's right\ldots  I'm saying she saved my life.  I get woken up by bugs.  Writing on the wall.  I go climb in the tub and *BAM*.  Glassplosion.



\strong{\blacktriangleright  WhedonRipperFan}
Replied on July 7th, 2011:
This conversation's going nowhere.  She's bad.  But she fought an Endbringer!  But that doesn't change the fact that she's bad.  But she saved lives!  But that doesn't change the fact that she's bad.  But she keeps the peace!
Aside:  Anyone else find it really funny that we're talking about Skitter being powerful like we used to talk about Kaiser and Lung?  If you'd told me the gawky bug girl was going to be one of the scariest motherfuckers in town, I wouldn't have believed you.



\blacktriangleright \strong{XxVoid_CowboyxX}Replied on July 7th, 2011:
I wouldn't have either.



\blacktriangleright \strong{Bruce Lao }(Brockton Bay Refugee)
Replied on July 7th, 2011:
Easy to be one of the scariest people around if you're one of the only people around.  It's a question of surviving, and the Undersiders are the types who can get away from trouble, so they outlast the opposition.  How many capes are even left, now?



\blacktriangleright \strong{Nondeceptive} (At Ground Zero: Brockton Bay)
Replied on July 7th, 2011:
Makes you wonder what she's like in real life.  Who's the woman behind the mask (assuming woman from height)?  What's her day job?\strong{ }



\blacktriangleright AntigoneReplied on July 7th, 2011:
She lives in the North end (apparently, first sighting, current location), slightly-above average height woman.  Slender.  Personality?  No idea.  What do we even know of her personality?



\sectionbreak



Greg stopped scrolling down the page.  The computer screen glowed in his dimly lit bedroom.



``A woman of above average height\ldots or a tall teenager,'' he mumbled to himself.  ``North end, lives in the area.  Personality\ldots vicious, smart, tough, a little unhinged?''



The image clicked.  A girl he'd had classes with, what felt like ages ago.  Taylor Hebert.



He'd thought maybe he had a shot with her, once.  Only she'd brushed him off.  It had bugged him more than it should have.  Why couldn't it be like it was in the movies and on TV?  Why couldn't the geeks band together?



He thought briefly of GstringGirl, felt a pang of disappointment and a momentary digust.  She'd refused the offer to meet up, then had turned down his request for a picture, or a webcam chat.  The conclusion had been obvious.  A creep.  A liar.



The name should have been a giveaway, but he'd held on to a shred of hope that there really was a girl out there more into gaming, coding and finding cool stuff on the web than on being `cool' and going out on Friday nights.



Was Taylor a creep of an entirely different sort?  A degenerate villain?  An \emph{upstanding} villain?  He could visualize her, sitting in class, tense with anger and frustration, the lines of her face hard as she bottled up a million little indignities and more than a few big ones.  It wasn't that hard to imagine.  Was Taylor \emph{Skitter}?



If he'd figured it out, others would too.  Or they would soon enough.  Her parents – did they know?  They had to.  How could they \emph{not}?  Others.  Who else might have paid enough attention to Taylor to guess?  The girls who had been bullying her?  Maybe, maybe not.  Now that he'd thought about it, it was impossible to shake the idea.  But the bullies maybe didn't know the real her, didn't see the \emph{person}.



There was no way people wouldn't start connecting the dots.  Not with the eyes of the whole city, the whole \emph{country} on her.  Leader of a villain organization that had claimed a town and driven out all comers.  Ruthless, standing up against Endbringers and the Slaughterhouse Nine.



He wheeled his computer chair away from the desk.  His eyes fixed on the bulletin board to his left.  A poster for Ransack took up half of it, and other scraps of paper took up more space.  A checklist of unlocks to get for the game, the ad for the computer class he was taking, and in a space all on its own, an information sheet.  The remaining summer months would feature special arrangements for classes, to make up for the weeks of classes students had missed in the wake of the Endbringer attack.



The eighth of July.  Tomorrow.



Did she plan to go?  Was she aware of how much attention people were paying to her?



He could imagine himself in her shoes and could almost guess.  To actually have some confidence, after having none for so long?  To have a second chance?



In her shoes, he'd do it in a heartbeat.





