





``Ballet, horseback riding, modeling classes or violin.  Pick \emph{one}, Emma.  \emph{One}.''



``Or, or, or, maybe I don't pick \emph{any}, and\ldots''



``And?'' she could hear a weariness in her father's voice.  He checked over his shoulder and then turned the car into a side street.  A bag with assorted tubs of ice cream sat on the divider between the pair of them.



``Maybe you give a second thought to moving?   There's really nice places just a little way South, and I'd still be going to the same school, and-''



``Nope.''



``Dad!''



``There's three jobs I absolutely despise in this world.  One is matching socks, the second is ironing, and the third is moving.  I can foist the first two off on your mom, but the third is a \emph{lifestyle} choice.  My lifestyle, specifically, is owning the house I'm going to live in until I die.''



Emma frowned, turning to look out the window.  She pouted a little, ``This place sucks.  Brockton Bay sucks.\emph{``}



``What's so bad about it?''



``Everything's falling apart.  It's like\ldots show me any house, and I can point out ten things that are wrong with it.''



``Every house has something wrong with it.''



``Not every house!  Like, when I went to Chris' birthday party?  I-''



``Chris?''



``Christine,'' Emma injected a note of condescension into her voice, ``Last weekend?  Or did you forget already?''



``Why not call her Christine?  Perfectly nice name.''



``Because androgyne is \emph{cool}, dad.  It's the thing in modelling.  Like, I could never have my hair short, but-''  She stopped mid-sentence, answering her phone mid-ring.  ``Hello?''



``Emma!''  The voice on the other end was breathy, excited.  There was a babble of other voices in the background.  She could imagine the other youths lined up to use the pay phones.



``Taylor,'' Emma said, smiling.



``Ok I gotta talk fast because I only have two minutes and I need my other fifty cents to call my dad.  We rowed across the lake this morning to this waterfall, only it wasn't exactly a water\emph{fall}, more like a water stair, and we were all taking turns sliding and falling down this set of slick rocks, and Elsa, she's this girl wearing a bikini, she's been spending the last three days acting like she's hot stuff, she slides down the wrong part, and it catches on the strap, right?  It doesn't tear it off, but it \emph{stretches, }so it doesn't even fit her anymore\emph{\ldots}''



Emma laughed, leaning back against her car seat.



It was something of a relief, to hear Taylor getting excited about something, to hear her getting excited over \emph{nothing}.  She'd lost her mother a year ago, and hadn't bounced back, not entirely.  Her smiles not quite as wide, she was a second later to laugh, as if she had to wait, to give herself permission to do it, had to hold back.  Before, it had been almost no holds barred.  Anything went, however they wanted to amuse themselves, whatever they wanted to talk about.  Complete and total openness.  Lately there had been too many movies, too many activities and topics of conversation, that Taylor preferred to avoid.



It hadn't been easy, Emma mused, as Taylor yammered on.  Sometimes she'd call, they'd do their customary hanging out, and she'd feel like the time was wasted, afternoons and weekends spent with her best friend that she didn't enjoy.



Not that Taylor was a wet blanket, but, like, maybe she was a \emph{damp} blanket?



This?  This inane, aimless, stupid, one-sided conversation where she'd said\emph{ one} word?  This was the good stuff.  It gave her hope that things could get back to normal.



``\ldotsand I wish I'd listened to my dad, because he suggested at least ten times that I might want to take more books, and I only brought three, and I've read each of them twice already.  My\ldots''



Taylor's voice continued over the phone, but Emma felt her dad's hand on her wrist, lowered her phone to pay more attention to her surroundings.



The car had stopped in the middle of a narrow one-way street.  A dumpster had been shifted to block the end of the alley.



She looked over her shoulder, down the other end of the alley.  A white van had stopped there, the taillights glowing.  There were a group of twenty-something Asian-Americans approaching, sliding over the hood of the van to get into the alley and approach.  Members of the ABB.



\emph{This isn't supposed to happen in broad daylight}, Emma thought.



Taylor's voice was faint, ``\ldotsI could probably recite this one book word for word for you by the time I get back.  Maybe if I asked one of the counselors, I could get more.''



Her heart pounding as hard as it ever had, Emma hung up.  Some part of her rationalized it as needing to eliminate the distraction, to focus on the more immediate problem.



``Hold tight,'' her father said.



She did, and he put his foot to the gas.  The car started rolling toward the dumpster, and the gang members behind them began running after them.



\emph{Too slow}, she thought.



The car barely tapped the dumpster.  It was only after contact had already been made that her dad put his foot on the gas, pushing against the blockade instead of ramming or crashing into it.



The dumpster didn't budge.



\emph{They blocked it.  Or they took the wheels off}.  \emph{Or both}.



There were too many people behind them for the car to reverse.  Not unless her dad wanted to hurt or kill a bunch of people.  Even if he did want to hurt them, he couldn't be sure he'd hit them, and where could he go?  There wasn't any guarantee he'd be able to move the dumpster if he backed up and rammed into it.



``Call the police,'' her father said.



She barely registered it.



``Emma!  Call the police!''



She fumbled with the phone.  Nine-nine\ldots



\emph{Why won't my hands work?}



Nine-one-one.



The window to her right shattered.  She screamed, then screamed again as hands clutched her hair, hauled her partially out of her seat, until the seatbelt strained against her shoulder and pelvis.  He wasn't strong enough to actually lift her, but it \emph{hurt}.  She wasn't thinking, only wanted the pain to stop.  Her mind was flooded with images of what might happen if the person outside tugged in a slightly different direction and dragged her face against the broken glass of the window.  The phone clattered to the floor as she gripped her attacker's wrists, tried to alleviate the pain of hair tearing free from her scalp.



She put her feet flat on the floor of the car, pushed herself up and away from her seat, almost \emph{helping} her attacker.



Emma regretted it almost as she did it, but in the panic and pain, she undid the seatbelt.



She'd just wanted the pain to stop, and now there were two sets of hands gripping her, hauling her up and out through the car window.  Glass broke away against the fabric of her denim jacket, and she fell hard enough against the pavement that grit was pushed into her skin.



\emph{I hope the jacket didn't get torn.  It was so expensive}, she thought.  It was inane, stupid, almost hilariously out of sync with reality.  \emph{Delirious.}



Her father's screams of almost mindless panic sounded so far away, as he cried out her name, over and over again.



The gang members who stood above her each wore crimson and pale green.  There were other colors, predominantly black, but the constrast of red and green stood out.  Some had their faces exposed, others wore kerchiefs over the lower halves of their faces.  One had a bandanna folded so it covered one eye.  She couldn't think straight enough to count them.



They had knives, she belatedly noted.



Her father screamed for her again.



\emph{Stop, dad.  You're embarassing me}.  She was more cognizant of how irrational the thought was, this time.  Odd, how \emph{calm} she felt.  Except that wasn't right.  Her heart was pounding, she could barely breathe, her thoughts were jumbled and irrational, and yet she somehow felt more together than she might have guessed she would.



She wasn't hysterical, at least.  She was oddly pleased with that, even as she wondered if she might wet herself.



``Turn over, ginger bitch,'' one of the girls standing above her said.  The order was punctuated by a sharp kick to Emma's ribs.



She flopped over, face pressing against the hot pavement.  Hands took hold of her jacket and pulled it off.  The sleeves turned inside out, the half-folded cuffs catching around her hands.



If she'd been taking it off herself, that would have been cause for some rearrangement, to get her hands free.  Instead, they pulled.  It hurt briefly, and then they had the jacket.



``Here, Yan,'' one of the guys said, his accent almost musical.  ``You owe me.''



``Sweet!''  The voice sounded young.



\emph{My jacket}, Emma thought, plaintive.



``We could send this bitch out of town,'' one of the guys said.  ``Stick her in one of the farms and hold her for a while.  She's got tits, could auction her off.



``Don't be a moron.  White girl goes missing, they \emph{look}.''



Someone opened the car door and climbed in.  There was the sound of the glove compartment opening, of items falling to the floor, where her cell phone was.



For the life of her, she couldn't remember if she had hit `call' on her cell phone before she'd dropped it.  It would mean the difference between her phone sitting on the floor of the car, the numbers displayed on the screen, and authorities using the phone to find her location, sending help.



Someone grabbed her hair, again.  This time, there was a tearing sensation, and the tugging abruptly stopped.  Her face cracked against the pavement beneath, one cheekbone catching almost all of the impact.



They'd cut her hair, and she'd just bruised her face.



``Face,'' she mumbled.



``What's that, ginger?'' the girl standing over her asked.  Emma twisted her head around to see the girl holding a length of red hair in her hand.



``Not- not the face, please.  I'll do anything you want, just\ldots not the face.''



It was the delirium that had taken hold of her the second her father had seized her arm.  It wasn't really her, was it?  She couldn't be this stupidly vain when it all came down to the wire.  She didn't want to be that kind of person.



``You'll do \emph{anything}?'' One of the guys asked.  The one with one eye.  ``Like what?''



She reached for an answer, but her thoughts were little more than white noise.



The answers that \emph{did} come to mind weren't possibilities.  Not really.



``Then it's the face after all.  Hold her.''



Ten minutes ago, she'd never been afraid.  Not \emph{really}.  Stage fright, sure.  Fear of not getting the Christmas present she wanted?  Sure.  But she'd never been \emph{afraid}.



And before the one-eyed thug spoke that last sentence, she'd never known \emph{terror}.  Had never known what it might be like to be a deer in the moment the wolves set tooth to flesh, the rabbit fleeing the bird of prey.  It was like being possessed, and the white noise that had subsumed her her thoughts when she searched for an argument now consumed her brain in entirety.  She felt a kind of surge of strength as her fight or flight instincts kicked into gear, and it wasn't enough.



She was outnumbered, and many of them were stronger than her, even with the adrenaline feeding into her.  Two held her arms out to either side, and someone knelt just behind her, knees pressing hard against the side of her head, keeping her from turning it.  Looking up, she could see a girl, not much older than her, sporting a nose ring and a startling purple eye shadow.  She was wearing Emma's jacket.



Emma could hear her father screaming, still, and it sounded further away than ever.



One-eye straddled her, planting his left hand on top of her hair, helping to hold her head down to the ground.



He held a knife that was long and thin, the blade no wider across than a finger, tapering to a wicked point.  What was it called?  A stiletto?  He rested the flat of the blade on the tip of her nose.



``Nose,'' he murmured.  The blade moved to her eye, and she couldn't move away.  She could only shut it, feel it twitching mercilessly as he laid the flat of the blade against her eyelid, ``Eye\ldots''



The blade touched her lips, a steel kiss.



``Mouth\ldots''



He used the blade to brush the hair away from the side of her head, hooked an earring with the point of the blade.



``Well, you can hide the ears with the hair,'' he said, his voice barely over a whisper.  The knife point pulled at the earring until her face contorted in pain.  ``So maybe I'll take both.  Which will it be?''



She couldn't process, couldn't sort out the information in the mist of the terror that gripped her.  ``Unh?''



Again, the knife traveled over her face, almost gentle as it touched the areas in question.  ``One eye, the nose, the mouth, or both ears.  Yan here thinks she has what it takes to be a \emph{member}, instead of a common whore, so you choose one of the above, and she goes to town on the part in question, proves her worth.''



``Holy shit, Lao,'' the girl with the eye shadow said.  She sounded almost gleeful, ``That's fucked up.''



``\emph{Pick},'' he said, again, as if he hadn't heard.



Emma blinked tears out of her eyes, looked for an escape, an answer.



And she saw a figure crouched on top of her father's car, dressed in black, with a hood and a cape that fluttered out of sync with the warm sea breeze that flowed from the general direction of the beach.  She could see the whites of the girl's eyes through the eyeholes of what looked like a metal hockey mask.



\emph{Help me}.



The dark figure didn't move.



Lao, the one eyed man, reversed the knife in his hands and handed it to the girl with the eye shadow.  The girl, for her part, dragged the knife's point over Emma's eyelid, a feather touch.



``Pick,'' the girl said.  ``No, wait\ldots''



She shoved the handful of hair she'd cut away into Emma's mouth.  ``Eat it, \emph{then} pick.''



Emma opened her mouth to plead for help, but she couldn't find the breath.  The hair wasn't it, not really.  Some of it was the weight of the young man sitting on her chest, crushing her under his weight.  Mostly, it was the fear, like a physical thing.



She thought of Taylor, of all people.  Taylor had, in her way, been put to the knife, had had an irreplaceable part of herself carved away.  Not a nose or an eye, but a mother.  And in the moment she'd found out, a light had gone out inside Emma's best friend, a vibrancy had faded.  She'd ceased to be the same person.



If she'd experienced her first real taste of fear when the gang members attacked the car, her first real taste of terror when Lao proclaimed he'd cut her face, then it was the thought of Taylor, of \emph{becoming} Taylor, that gripped her with \emph{panic}, a whole new level of fear.



\emph{I won't become Taylor}.



\emph{I'm not-}



\emph{I'm not strong enough to come back from that.}



The knife momentarily forgotten, she bucked, thrashed, fought.  An inarticulate noise tore out of her throat, a scream, a grunt, and a wail of despair all together, an ugly sound she couldn't ever have imagined she'd make.  Lao was dislodged, one hand freed, and she brought it up, not in self defense, but to attack.  Her nails found his one good eye, caught on flesh, dug into the softest tissues she could find and dragged through them, through eyelid and across eyeball, through cheekbone and the meat of his cheek.



He screamed, struck her with enough force that she wondered if he'd had knuckle dusters she hadn't seen.



Knuckle dusters\ldots a weapon.  She belatedly remembered the knife, looked up at the girl with the eye shadow.



The figure in the black cloak had the knife-wielding girl, the knife hand twisted behind the girl's back.



With a sharp, calculated motion, the arm was twisted a measure too far, the eye shadow girl jerked off balance so the weight of her body would only help twist it further.  The girl screamed, dropping the knife, and she flopped to the ground, her arm gone limp, dangling from the shoulder at an angle that shouldn't have been possible.



The figure in black turned on Lao.  She swept her cape to one side, and momentarily became a living shadow, a transparent blur.  When she returned to normal, her posture was different, and the knife had disappeared from the ground.  It was in her hand.



Emma watched in numb horror and awe as the girl advanced on Lao, who crab-walked backward to get away.  She closed the distance, stretched out one arm, and delivered a single scratch with the knife, cutting into Lao's right eye.



Other thugs had already fallen.  The one who'd held her arm before she pulled it free was slumping over, unconscious.  The woman who must have been standing next to Emma's father, was lying prone on the ground on the other side of the car, a pool of blood spreading beneath her.



That left only one, the thug who'd held Yan's left arm.  He was on his feet in a moment, running, Emma's backpack in one hand, open, the contents from the glove compartment falling free.  Useless, trivial items.  A bag of candy, the driver's handbook.  Things he'd taken only because he \emph{could}.



The girl in the cloak was small, Emma noted.  Younger.  Again, the cloaked vigilante became a virtual living shadow, flung herself down the length of the alleyway, faster than the man was running.  She moved past him, ducking low as she materialized into a normal form.  The knife raked across the side of his knee, and he fell.  He twisted as he hit the ground, kicked out with one leg, and caught the girl in the side of one knee.  She tumbled landing on top of him.



The ensuing struggle was brief and one sided.  He tried to grab his attacker, found only immaterial shadow.  He turned over, getting on hands and knees to push himself to a standing position, but she moved faster, going solid as she loomed over him, one hand on the wall for balance.  She tipped, let herself fall, and drove his face into the pavement with all the weight she could bring down on him.



A second later, the cloaked girl was holding one of his hands against a door just to his right.  She used the stiletto to impale his hand to the wood, bent the blade until the handle snapped away.



``Emma,'' her father said.  He was out of the car, embracing her.  ``Are you hurt?  Emma?''



One hand absently tried to claw her own strands of hair from her mouth, failing to get all of them.  She settled for leaving the hand mashed against her mouth, as incoherent a gesture as anything she might have said if she'd been able to speak.



Wordless, the girl in the black cloak limped a few steps away from the fallen boy before adopting her shadow form, floating away, untouchable.



\sectionbreak



``Emma?''



Emma stared at her bedroom ceiling.  It was her sister's voice.



``I went to that store, got that shampoo you liked.''



Emma turned over, pulling the covers tight, staring at the wall instead.



``I just thought a shower must sound pretty good right about now.''



There were still scraps of paper stuck to the wall with blue tack, the corners of the posters she'd torn down in a fit of emotion.  All the words in the English language, and there wasn't one for what she'd felt.  Not anger, not fear, not resentment\ldots some combination of those things that was duller, heavier, suffocating.  The eyes of the boys from the posters had been too much.



``\ldotsOkay,'' her sister said, from the other side of the bedroom door.  ``We love you, Emma.  You know that, right?''



\sectionbreak



Her mother spoke through the door, ``Emma?  Taylor's on the phone.  She's still at summer camp.  Do you-``



Emma sat up in bed, swung her legs around until they hung off the end of the bed.



``No.''  Her voice was a croak.  How many days had it been since she spoke?



``If I explained, maybe she could-``



An image flashed across her mind's eye.  Taylor, on the other end of the phone, laughing, blabbering on, happy, just before the incident.



The tables had turned.



``If you tell her, I'm never coming out,'' she croaked.



There wasn't a reply.  Emma stood from the bed and approached the door.  She could hear her mother on the other side.



``-doesn't want to talk to you right now.  I'm sorry.''



A pause.



``No.  No, I don't.''



Another pause, briefer.



``Bye, honey,'' Emma's mom said.



Floorboards creaked as her mother walked away.



\sectionbreak



``\ldotsa therapist.  You could go alone, or we could go together.''



She grit her teeth.



``I\ldots I left her number by the phone.  We're all going to be out.  Your sister's at a thing related to the college dorms, a pre-moving in orientation.  Your mom and I have work.  You know our phone numbers, but I was thinking, uh.''



A pause.



``If you were thinking of doing something drastic, and you didn't feel like you could talk to any of us, the therapist's number's there.''



Emma hugged her knees.  Her back pressed hard against the door, the bones of her spine grinding against the door's surface.



``I love you.  \emph{We} love you.  The doors are all double locked, so you're safe, and there's food in the fridge.  Your sister bought that stuff from the store you like.  Soaps and shampoos.''



Emma clutched the fabric of her pyjamas.



``It's been a week.  You can't- you can't be happy like this.  We won't be here to bother you, so warm yourself up some food, treat yourself to a nice bath, maybe, watch some television?  Get things a step back to normal?''



She stood, abrupt, paced halfway across her bedroom, then stopped.  Nowhere to go, nothing to do.



She stood there, staring at the wall with the torn corners of poster still stuck to it, fists clenched.



``Bye, honey.''



She was rooted to the spot, staring at a blank surface, listening as her family went about their routines.  There were murmurs of conversation as they got organized, orchestrated who was going in which car, what everyone was doing for lunch.  Quieter fragments of conversation where they were discussing \emph{her}.



The door slammed, and she heard the locks click, a sound so faint she might have imagined it.



It was only after everyone had left that she ventured out of her room.



Coffee.  Cereal.  She went through the motions, reheating a mug of the former and preparing the latter.



She hadn't finished either when she stood and ventured into the bathroom.  She didn't touch the bag of expensive soaps and shampoos, instead using her father's regular shampoo.  She soaped up with the bar soap, rinsed off, then stepped out of the shower to dry herself.



Once she was dressed, her hair still damp, she approached the front door, hesitated.



She pushed through, left it unlocked behind her.  She couldn't shake the worry that if she stepped back inside to find keys, she might not be able to step through the threshold again.



Her teeth were chattering by the time she was at the end of the street, and it wasn't cold out.



Her thoughts were a chaotic jumble as she walked.  Her stomach felt like a blob of gelatin, quivering with every step she took.



The stares were worst of all.  As much as she tried to tell herself that she wasn't in the middle of a giant spotlight, that people didn't care, she couldn't shake the idea that they were watching her, analyzing her every move, noting her wet hair, noting the hunk of hair at the back that was shorter than the rest, crudely chopped off.  Were they seeing her as a \emph{victim}, someone so full of fear and anxiety that her every movement practically screamed `easy target'?



Perhaps the dumbest insecurity of all was the worry that somehow they could read her mind, that they \emph{knew} she was doing the dumbest thing she'd ever done.



Every step she took, the white noise of her fear consumed a bit of her rational mind.



She found herself back at the mouth of the narrow one-way road.  The dumpster had been moved, the van was nowhere in sight.



This was different from feeling like a victim, because here, she knew she really \emph{was} begging to be attacked.  To loiter around in known gang territory, unarmed?  It was senseless.  This time, they might really carry through with their threats.  All it would take was the wrong person seeing her.



Emma couldn't bring herself to care.  She was scared, but she was scared every moment of every day, had been for the last seven days.  Right now?  She was more desperate than scared.



She'd hoped she would run into the girl in the black cloak.  She wasn't so lucky.  Her stomach started protesting that the half-bowl of cereal hadn't been enough, but she stayed where she was.  She hadn't brought a wallet, a phone or watch, so she had no way of getting food, nor any idea of how long she was really waiting.



When the sun was directly overhead, she turned to leave.



There was no place to go.  Home?  It would be too easy to shut herself in her room, to hide from the world.  There was nothing she wanted to do, nobody she wanted to talk to.



The world was an ugly place, filled with ugly scenes, and unlike before, she couldn't shut it out, couldn't shake the idea that something horrible was happening around every corner.  Thousands of people suffering every second, around the world.



What got her, the nebulous idea that haunted her, was the \emph{impact} those scenes had.  There were so many defining moments, so many crises, big and small, that shaped the people they touched.  The biggest and most critical moments were the sorts that wiped the slate clean, that ignored or invalidated the person who had existed before, only to create another.



Emma had fought in a moment of desperation, as if \emph{fighting} could make her stronger than Taylor, set herself apart.  Except she'd failed.  It was unbearable.  She hated herself.



Her eyes watched the crowd, searching for the people who were eyeing her, judging her.  She couldn't find any obvious ones, but she couldn't shake the belief that they were there.



``Takes guts.''



She could feel her heart leap into her throat, wheeling around, imagining the Asian girl with the eye shadow standing behind her.



It wasn't.  The girl was dark-skinned, slender, with long, straight hair.  She had a hard stare, penetrating.



``Guts?''  Emma couldn't imagine any word less appropriate.



``Coming back.  The only reason you'd do it is because you were looking for revenge, or you were looking for \emph{me}.  Or both, depending on how cracked you are.''



Emma opened her mouth, then closed it.  The realization hit her.  This was the girl with the black cloak, announcing herself.



She asked the question she'd gone to such risk to pose to the girl, ``Why\ldots why did you wait?  You saw me in trouble, but you didn't do a thing.''



``Because I wanted to see who you were.''



Before, Emma suspected she'd have been offended, aghast at the idea that this girl would leave her to suffer, leave her life at risk, just for an answer to a question.  Now?  Now she could almost understand it, oddly enough.  ``Who was I?''



``There's two people in the world.  Those who get stronger when they come through a crisis and those who get weaker.  The ones who get stronger naturally come out on top.  There's ups and downs, but they'll win out.''



``Who was I?'' Emma asked, again.



``You're here, aren't you?''  The girl smiled.



Emma didn't have an answer to that.  She shut her mouth, all too aware of the people walking past them, going about their everyday lives, overhearing snippets of their conversation and yet failing to pick up anything essential.



``I want to be one of the stronger ones.''



``I don't do the partner thing, or the team thing.''



Emma nodded.  She didn't have an answer ready.



The other girl's eyes studied her, and she seemed to come to a decision.  ``It's a philosophy, a way of looking at it all. You can look at the world as a\ldots what's the word?  One thing and another?''



``A binary?''



``A binary thing.  But not black and white.  It's about the divide of winners and losers.  Strong and weak, predators and prey.  I kind of like that last one, but I'm a hunter.''



Emma thought back to how readily the girl had taken the thugs apart.  ``I can believe that.''



The girl smiled.  ``And what you have to keep in mind, is the biggest question of all is one you're answering for yourself, right now.  Survivor or victim?''



``What's the difference?''



``On this violent, brutish little planet of ours, it's the survivors who wind up the strongest ones of all.''



\sectionbreak



Emma stood from the kitchen table, aware that her entire family was watching her.



\emph{It's all mental}.



Three weeks ago, she might never have imagined that she'd be able to resume life as normal, to not be afraid.



Perhaps it was more correct to say that she \emph{was }afraid, she just wasn't \emph{acting} it.  Faking it until she could make it the truth.



``You're going out?'' her sister couldn't quite keep the note of suprise out of her voice.



``Sophia's dropping by,'' Emma said.



\emph{Just want to forget it happened, put it behind me.  Move forward.}



``Taylor got back from camp this morning,'' her mother said.



Emma paused.  ``Okay.''



``She might stop by.''



``Okay.''



Emma couldn't resist hurrying a little as she collected her dishes and rinsed them in the sink.



``If she comes by when you're not here-''



``I'll talk to her,'' Emma said.  ``Don't worry about it.''



She made her way to the front hall, stopped by the mirror to run a brush through her hair.  It had all been cut to match the piece that had been cut shorter with the knife.



She couldn't wait for it to grow in, as that alone would erase just one more memory that reminded her of her moment of weakness and humiliation, of how close she'd come to dying or being mutilated.  Until it did grow in, it was yet another reminder of all the ugliness she wanted to be able to look past.



Sophia was waiting outside by the time she had her shoes on.



``Heya, vigilante,'' Emma said, smiling.



``Heya, survivor.''



She could see Taylor approaching, tan, still wearing the shirt from camp in the bright primary blue, with the logo, shorts and sandals.  It only made her look more \emph{kiddish}.  Broomstick arms and legs, gawky, with a wide, guileless smile, her eyes just a fraction larger behind the glasses she wore, a little too old fashioned.  Her long dark curls were tied into a loose set of twin braids, one bearing a series of colorful `friendship braclet' style ties at the end.  Only her height gave her age away.



\emph{She looks like she did years ago.  Way before her mom died}.  \emph{Like she's nine, not thirteen.}



``Who the fuck is that?'' Sophia murmured.



Emma didn't reply.  She watched as Taylor approached the gate at the front of the house, walked up the path to the stairs where she and Sophia stood.



``Emma!''



``Who the fuck are you?'' Sophia asked.



Taylor's smile faltered.  A brief look of confusion flickered across her face.  ``We're friends.  Emma and I have been friends for a long time.''



Sophia smirked.  ``Really.''



Emma resisted the urge to cringe.  \emph{Fake it until I make it}.



``Really,'' Taylor echoed Sophia.  The smallest furrow appeared between her eyebrows.  ``What's going on Emma?  I haven't heard from you in a good while.  Your mom said you weren't taking calls?''



Emma hesitated.



To just explain, to talk to Taylor\ldots



Taylor would give her sympathy, would listen to everything she had to say, give an unbiased ear to every thought, every wondering and anxiety.  Emma almost couldn't bear the idea.



But there would be friendship too.  Support.  It would be so easy to reach out and take it.



``I love the haircut,'' Taylor filled the silence, talking and smiling like she couldn't contain herself.  ``You manage to make any style look great.''



Emma closed her eyes, taking a second to compose herself.  Then she smiled back, though not so wide.  She could feel Sophia's eyes on her.



She stepped down one stair to get closer to Taylor, put a hand on her shoulder.  Taylor raised one arm to wrap Emma in a hug, stopped short when Emma's arm proved unyielding, stopping her from closing the distance.



``Go home, Taylor.  I didn't ask you to come over.''



She could see the smile fall from Taylor's face.  Only a trace of it lingered, a faltering half-smile.  ``It's\ldots it's never been a problem before.  I'm sorry.  I was just excited to see you, it's been weeks since we even talked.''



``There's a reason for that.  This was just an excuse to cut a cord I've been wanting to cut for a long time.''



There it went.  The last half smile, wiped from Taylor's expression.  ``I\ldots what?  Why?''



``Do you think it was \emph{fun}?  Spending time with you, this past year?''  The words came too easily.  Things she'd wanted to say, not the whole truth, but feelings she'd bottled up, held back.  ``I wanted to break off our friendship a long while back, even before your mom kicked the bucket, but I couldn't find the chance.  Then you got that call, and you were so down in the dumps that I thought you'd hurt yourself if I told you the truth, and I didn't want to get saddled with that kind of guilt.''



It was surprising how easily the words came.  Half truths.



``So you lied to me, strung me along.''



``You lied to yourself more than I lied to you.''



``Fuck you,'' Taylor snapped back.  She turned to leave, and Sophia stuck one foot out.  Taylor didn't fall, but she stumbled, had to catch the gate for balance.



Taylor turned around, eyes wide, as if she could barely comprehend that Sophia had done what she'd done, that Emma had stood by and watched it.



Then she was gone, running.



``Feel better?''  Sophia asked.



\emph{Better}?  No.  Emma couldn't bring herself to feel guilty or ashamed, but\ldots it didn't feel good.



That knot of negative emotion was tempered by a sense of profound relief.  One less reminder of the old, weak, pathetic vain Emma, one more step towards the new.



\sectionbreak



Emma's cell phone vibrated.  She rose from her bed, suppressing a sigh.



As quiet as she could, she collected the tackle box from beneath her bed, dressed and headed downstairs.



Her father was at the kitchen table.  His eyes went wide, and he stood.



She pressed her finger to her lips, and he stopped, his mouth open.



She hesitated, then spoke in a whisper, ``I need your help.  Please.  Can- can you not ask any questions just yet?''



He hesitated, then nodded.



She handed him the keys, and climbed into the passenger seat.



He started up the car, then drove in the directions she dictated, her eyes on the phone.



They found themselves downtown, in the midst of a collection of bodies.



And in the center, leaning against a wall, Shadow Stalker was hunched over, using her hands to staunch a leg wound.



Emma bent down, opened the tackle box, and began gathering the first aid supplies.



Wordless, her father joined her.



\emph{We owe her this, at least.}



\sectionbreak



``Give it back,'' Taylor's voice was quiet, but level.



``Give what back?''



``You guys broke into my locker.  You took my flute.  It's something my mom left me, something she used, that my dad gave to me so I could remember her.  Just\ldots if you've decided you hate me, if I said the wrong thing, or led you to believe something that wasn't true, okay.  But don't do that to my mom.  She was good to you.  Don't disrespect her memory.''



``If it was so valuable to you, then you shouldn't have brought it.''



Taylor didn't speak for long seconds.  ``Can you blame me?  Since school started, you've been\ldots after me.  As if you're trying to make a point or something.  Except I don't know what it is.''



``The point is that you're a loser.''



Taylor wasn't able to keep the emotion off her face.  ``\ldotsEven if it's just a flute and a memory, maybe I wanted to feel like I had some backup here.  I thought you were better than that, screwing with me on that level.''



``I guess you're wrong,'' Emma replied.  She let the words sit for a few seconds, then added, ``Doesn't look like she's offering you any backup at all.''



Emma had mused, back in the week she'd been reeling from her near-miss with death or disfigurement, that there were moments that changed destinies, that altered people's trajectories in life.  Some were small, the changes minor, others large to the point they were irreversible.  It was so easy, just to utter the words, and the reaction was so profound.  A mixture of emotions that briefly stripped Taylor bare, revealed everything in a series of changing facial expressions.



She didn't enjoy it.  Didn't revel in it.  But it was\ldots reassuring?  The world made sense.  Predators and prey.  Attackers and victims.  It was like a drug, only she'd never experienced the high, the pure joy of it.  There was only the withdrawal, the need for a hit just to get centered again.



\emph{Fight back, get angry, hit me}.



\emph{Challenge me}.



It took Taylor long seconds to get her mental footing.  She met Emma's eyes, and then stared down at the ground.  She mumbled her response.  ``I think that says a lot more about you than it does about me.''



\emph{That wasn't what I meant, }Emma thought.



She felt irrationally angry, annoyed, and couldn't put her finger on why.



It took her a minute to find Sophia, not helped by the fact that the two of them had classes on opposite sides of the building.



Sophia was putting coins into the vending machine.  She looked up at Emma.  ``What?''



``Did you break into her locker?''



``Yeah.''



``Stole a flute?''



``Yeah.''



Emma paused for long seconds.  To give the flute back, surreptitiously, it would go a ways towards breaking the rhythm, the cycle.



Taylor's words nettled her.  To back down now, it would be a step towards the old Emma, the victim.



``Fuck with it.  Do something disgusting to it, and make sure to wreck it so she can't use it ever again.''



Sophia smiled.



\sectionbreak



``Do you hereby attest that all statements disclosed in this document are the truth, to the best of your knowledge?''



``I do,'' Emma's father spoke.



Emma reached out and took his hand, squeezing it.  He glanced at her, and she mouthed the words, ``Thank you.''



There was a shuffling of papers at the other end of the long table.  ``We, the committee, have reviewed the documents, and agree that case one-six-three-one, Shadow Stalker, has met the necessary requirements.  With stipulations to be named at a future date, specific to her powers and the charges previously laid against her, she is now a probationary member of the Wards, until such a time as she turns eighteen or violates the terms of this probationary status.  Congratulations, Shadow Stalker.''



``Thank you,'' Shadow Stalker's tone was subdued, her eyes directing a glare at the center of the table rather than anyone present.



Emma watched as the capes and official bigwigs around her got out of their chairs, fell into groups.



Dauntless approached her dad.  She only caught two murmured words of Dauntless' question.  ``-divorce attorney?''



Shadow Stalker, for her part, stood and strode out of the room.  Emma hurried to follow.  By the time she reached the staircase, Shadow Stalker was halfway to the roof.



``You're angry.''



``Of course I'm angry.  Stipulations, rules and regulations.  I've had my powers for two and a half years and I've stopped more bad guys than half the capes in that room!''



Emma couldn't stop the \emph{memory} from hitting her.



\emph{The man struggled, and as much as Shadow Stalker was able to make herself immaterial, to loosen any grip or free herself from any bonds, she didn't have the ability to tighten that same grip.  He tipped backwards, off the edge of the roof, and a gesture meant to intimidate became manslaughter.}



Shadow Stalker stared off the edge of the roof at the body, then turned to look at Emma.



\emph{``Is- is he?''  Emma asked.}



\emph{``Probably best if you don't come on patrol with me again.''}



``You have,'' Emma replied, snapping back to reality.  \emph{How many have you `stopped'?}



``It's like putting a wolf among sheep and expecting it to bleat!''



``It's only three years.  Better than prison.''



``Three years and four months.''



``Better than prison,'' Emma repeated herself.



``It \emph{is} prison, fuck it!''



``It's like you said.  Just\ldots just fake it until you make it the truth, put away the lethal ammunition for a few years.''



Shadow Stalker wheeled on her, stabbed a finger in her direction, ``Fuck that.''



Emma stared at her best friend, saw the look in Sophia's eyes, the anger, the hardness.



For a moment, she regretted the choice she'd made.



Then she had her head in order again, the little things she was faking contorted with reality until she couldn't tell the difference anymore.



People could convince themselves of anything, and there were worse things than convincing oneself that they were strong, capable, one of the ones on top, rather than one of the ones on the bottom.



\sectionbreak



The door of the bathroom stall swung open.  Sophia had flung one arm around Emma's shoulders, and Emma joined her in laughing.  To their right, the third member of their trio was giggling so hard she had hiccups.



Taylor kneeled in the middle of a massive puddle of juices and sodas, some of it still fizzing around her.  She was drenched, head to toe, trickles still running off of the lengths of her hair.  Her style of dress had changed over the past little while, in ways Taylor probably wasn't fully aware of.  She wore darker clothes now, cloaked herself in sweatshirts and loose fitting jeans.  Her long hair was a shield, a barrier around her face.  All measures to hide, signals and gestures of defeat.



More than that, she'd changed in behavior, had stopped fighting back. She'd stopped \emph{reacting}, for the most part.  Her expression was impassive.  It took some of the fun out of it.  It was almost disappointing.



\emph{I'll have to think of a better one than this.  Crack that facade, }Emma thought.  She smirked as Madison led the way out of the bathroom, and they left Taylor behind.



\emph{Taylor had become the archetypical victim,} Emma mused, in one sober moment, as she parted ways with the other two girls, \emph{and I've found myself becoming the type of person who could genuinely laugh at something like this.}



She dismissed the thought, shifting mental gears, re-establishing the construction of self confidence she'd built.\emph{  }It was a little easier every time she did it.



\sectionbreak



The fan on the other side of the room had a piece loose.  It squeaked on every third rotation.



She examined her nails, picked at a fleck of something white that had stick to the end of one nail, then checked her cuticles.



The fan squeaked, and she turned her head, as if she could spot the offending flaw and fix it.



``You come all this way, and you don't have anything to say?''  Sophia asked.



Emma shrugged.  \emph{It was on our way}.



``Say what's on your mind.''



``It's all backwards, isn't it?''



``Backwards how?''



``Upside down, Turned around.  Two wrongs make a right.''



``What wrongs?''  Sophia's voice was hard.



``Not you.  Not your thing.  That's not what I'm talking about.  We're moving back to Brockton Bay.  As in, it's in progress.  Half our stuff's still back in Portland, half's in the Bay.  We finally moved.''



``Someplace nice?''



``Further north.''



Sophia smirked.



``But that's why I'm saying it's all backwards.  Things got flipped around.  The north end is \emph{nicer}, now.  They're rebuilding, and it's all coming together.  Downtown is the place that got hit hard.  You've got three big areas you can't go, with the crater, the quarantine and the place I heard people calling the scar, where they did some bombing run with Bakuda's stuff.  Construction's slower towards the south, because there's so much traffic and not a lot of roads.''



``Huh.''



``The bad guys are keeping the law, but things are \emph{better}, and you talk to anyone, there's \emph{hope}.  I don't know how that happens, how you visit every tragedy imaginable on a place, drop a dozen different nightmare scenarios on it, and things get \emph{better}.  How does that work?''



``I don't really care,'' Shadow Stalker said.



``It's your city.''



``The world ends in less than two years.  I won't be out of here before then.  I\ldots what's the word?  I \emph{reiterate}, I don't really care.''



``I'm trying to make conversation.''



``You're doing a shitty job of it,'' Sophia replied.



Emma shut her mouth, stared at her friend.



``World ends in two years,'' Sophia added.  ``It's a joke, pretending like things are getting better, like there's hope.  The world turns a few hundred more times and then it all ends.''



\emph{Sour grapes?}



``It's kind of neat in terms of the big picture,'' Emma said, ignoring Sophia.  ``It's like, the future hasn't looked this bright in a while.  There's promise, if this rumor about an open interdimensional portal is for real.  \emph{Multiple} portals, if you believe the really out-there rumors.  Escape routes, resources, work.  And Brockton Bay is at the center of it all.''



Sophia snorted.



``And, more than that, it's like, if we're talking about hope, about the future, who's more iconic for all that than \emph{kids}?  You know, that line about how kids are the future?  Heroes too, they're icons of hope too.  And put those things together, you get Arcadia High.  Winslow High's gone, and there's not quite enough students, so they're herding us all together.''



``So?''



``So, it's like, all this hope, you've got Brockton Bay at the center of it all.  And at the center of Brockton Bay's hope, it's Arcadia High.  And at the center of \emph{that}?  You've got the heroes and the winners.  I fully intend to be the latter.  In a way, it's like being queen of the world.''



``The popular kid in high school?''



``In \emph{the} high school,'' Emma said.  She shrugged.  ``It's one way of looking at it.''



``It's sad.''



Emma smirked.  ``\emph{Someone's }grumpy.''



``It's sad because you're making a fool of yourself, you're missing a key detail.''



``Which?''



Sophia shrugged.  ``Better if you find out for yourself.  I won't spoon-feed you.''



Emma rolled her eyes.  Sophia was just toying with her head.  Easy enough to ignore.



``I'm going to go.  I'd say it's been a pleasure, but\ldots''



Sophia caught the `but'.  ``Bitch.''



``Yeah.  Def,'' Emma replied, before hanging up the phone.  She stood from the stool that was bolted to the floor, stretched, then offered a small wave.



Sophia raised both hands together to offer a miniscule wave with her right.  They were cuffed together, LEDs standing out on the cuffs, marking the live current.



Emma couldn't tell herself she'd be back.  To stick around and be loyal now would betray every reason she'd given herself for dropping Taylor as a friend.  Taylor had been a wet blanket, a loser.  Sophia was no better, now.



It was ironic, but Sophia had proven herself to be more prey than predator, in the very philosophy she'd espoused.



\sectionbreak



``Hey dad?''



Her dad turned his head to acknowledge her, while keeping his eyes on the road. ``What is it?''



``Mind making a detour?  I wouldn't mind seeing Taylor's house.''



``I thought you weren't friends anymore.''



Emma shook her head.  ``I'm\ldots trying to put it all into perspective.  It's really changed, and it's easiest to get my head around the changes if I can look at the familiar places, and her house is pretty familiar.''



``Sure.  If nobody else minds?''



There were no objections from her mom or sister.



The city had always had its highs and lows, its peaks and valleys, but it seemed it was an even starker contrast now.  She'd commented, once, that for any one house, she could find three things wrong with it.  It had been flipped around, in its own way.  For every ten houses, there was one ruin, a dilapidated structure or pile of wreckage.  For every ten stretches of road that were intact, there was one that a car couldn't pass over.



They turned off Lord Street, onto the street that Taylor's house was on.



As they approached, Emma could see Taylor helping her dad unload a box from what looked to be a new or newly washed car.  He said something and she laughed.



The casual display of emotion was startling.  It was equally startling when, in the moment Emma's dad slowed the car down, Taylor's head turned, her eyes falling on them, her head and upper body turning to follow them as they passed.



She didn't even resemble the person Emma had known way back then, not the girl who'd approached her house after coming back from camp, and not the girl who'd been drenched in juice.  The lines of her cheekbones and chin were more defined, her skin baked to a light tan by the sun, her long black curls grown a touch wild by long exposure to wind.  Light muscles stood out on her arms as she held a box, her dad standing back to direct.



Even her clothes.  She wasn't hiding under a hood and long sleeves.  A trace of her stomach was exposed between the bottom of her yellow tank top and the top of her jeans.  The frayed cuffs were rolled up at the bottom, around new running shoes, and neither Taylor nor her dad seemed to be paying any attention to the knife that was sheathed at her back.



It surprised Emma, all the little clues coming together to point to one fact; that Taylor had \emph{stayed.}  She'd stayed, and she'd come out of it okay.  Judging by the new car, the shoes and her clothes, the Heberts were doing better for money than they had been the last time Emma had run into either of them.  Were they early beneficiaries of Brockton Bay's upswing in fortune?



It unsettled her, and she had a hard time putting her finger on \emph{why}.



It didn't hit her until they'd reached their new house, a recollection of something Sophia had said.



\emph{On this violent, brutish little planet of ours, it's the survivors who wind up the strongest ones of all.}





