





Tattletale stood at the very edge of the floor, with a twenty-five story drop just in front of her.  The wind whipped her hair around her, and she didn't even have a handhold available.  Shatterbird had cleared out all of the window panes, long ago.



She lowered her binoculars.  ``He's gone.  If he was going to pull something off, he'd want to watch and make sure everything went off without a hitch.''



``I could have gone with them,'' Imp said.  ``Listened in.''



``Not without us knowing their full set of powers,'' Tattletale said.



Imp folded her arms, pouting, ``I thought you were one of the cool ones.''



``Othello's a stranger,'' Tattletale said.  ``I'd think he has an imaginary friend who can mess around with us, but I didn't see any sign of anyone invisible walking around.''



``Isn't that the point?'' Regent asked.



``No dust or glass being disturbed, none of that.  I might think his `friend' is invisible and intangible, but then what's the point?  Accord tends to have people with \emph{good} powers.  Citrine, only bits I could figure out were that she's got an offensive power, something with \emph{substance}, and her focus was in a strange place.  She was more focused on \emph{places} in the room where the strongest powers were clustered, and her focus was fairly indiscriminate beyond that.  Either her power wasn't anything that \emph{anyone} here would have been able to defend against, like Flechette's arrows or a controlled version of Scrub's blasts, or she's a trump classification.''



``What's that?'' Regent asked.



``Official classification for capes who can either acquire new powers on the fly,'' Tattletale gestured towards Grue, ``Have an interaction with other powers that can't be categorized or they nullify powers.''



``She's powerful, then,'' Regent said.



``She \emph{acts like} she's powerful,'' Tattletale said, ``And she probably is.  But that database of PRT records we had didn't have anything in it about those two.  I don't know where he finds those guys, but Accord collects some damn heavy hitters.''



Parian broke her spell of silence.  ``You keep talking like we're going to fight them.''



``Threat assessment,'' Tattletale said.  She made her way back to her chair, sitting at the long table.  ``Be stupid not to know what we're getting into, especially with someone like him.''



``Not to mention we've gotten in fights with pretty much everyone who ever set up shop in the `Bay,'' Regent commented.



``There's nothing imminent,'' Grue said.  ``Let's focus on more immediate problems.''



He turned his attention my way.



``Me?'' I asked.



``He's right.  We've been so busy preparing for possible fallout that we haven't had time to discuss this,'' Tattletale said.



``I'm a non-factor.  The damage is done, and it's a question of the dust settling,'' I said, staring down at my gloves.  I'd altered some of my costume, but the real adjustments would have to wait until I had time.  I'd made up the extra cloth in an open area of my territory I was devoting to the purpose, but hadn't had time to turn it into something to wear for tonight.  Some of my mask, the back compartment of my armor and my gloves were more streamlined.  Or less streamlined, depending on how one looked at it.  Sharper lines, convex armor panels that flared out more, gloves with more edges for delivering damage if I had to get in a hand to hand fight.



I'd only done some of the armor, pieces of my costume that were already battered and worn.  My gloves, my mask and the back compartment of my armor tended to take the most abuse.  I'd update the rest later.



``I'm not sure it's that simple,'' Grue said, his voice quiet.  He reached across the table and gripped my hand, squeezing it.  ``Have we double checked to see what bridges they've burned for us?  My parents aren't showing any sign of interference.''



``Mom wouldn't care either way,'' Aisha said.  ``She might try to capitalize on the attention with appearances on television if she could get money for it.''



``Yeah,'' Grue agreed.



``My family wouldn't care,'' Tattletale said.  ``I'd be surprised if they didn't already know.  They'd choose to ignore it, I'd bet.  Parian?  You've covered your bases.''



``Most of my family is dead.  The ones who aren't dead already know,'' Parian said.  She looked out toward the window, at the city lights under the night sky.



Tattletale nodded, ``Let's see\ldots Rachel isn't a problem, not really.  Never had a secret identity.''



Rachel shrugged.  Her attention was on her dogs.  They were shrinking, their extra mass sloughing away.  She already had Bastard sitting next to her, his fur spiky and wet from the transformation.



``And if they tried to come at me through my family, they'd get what they deserved,'' Regent said.



``Why?'' Parian asked.



``His dad's Heartbreaker,'' Tattletale said.



``Oh.  Oh wow.''



``Funny thing is,'' Regent said, ``If you think about it, we might be bigger than Heartbreaker, now.  People all over America know who we are, and I'm not sure if Heartbreaker is known that far to the south or west.''



``That's not our focus right now,'' Grue said, squeezing my hand.  ``It's good that we're talking about safeguards and damage control, but discussing villains and the rest of America can wait.  They came after Skitter while she was out of costume.''



``How are you coping?'' Tattletale asked, leaning forward over the table.  ``You were pretty heavy-handed tonight.  We discussed it, sure, but I thought you'd at least \emph{pretend} to play ball with them.''



``I didn't need superpowered intuition to figure out they weren't going to cooperate no matter what I said,'' I replied.



``But you were provoking them.  Valefor especially.  You up for this, with all the other distractions?''



``This is what I've got left, isn't it?  The good guys decided to play their biggest card.  They couldn't beat Skitter, so they beat \emph{Taylor}.  As far as I'm concerned, there's no reason not to throw myself into this, to deal with both heroes and villains as a full-time thing.  I lay down the law, because now I've got time to enforce it.  I can be stricter with the local villains, back you guys up if they cause trouble, and dedicate the rest of my time to my territory.''



``Dangerous road to travel down,'' Tattletale said.  ``You need to rest, to have downtime.''



``And do what?  Go to a movie?  I'm not sure if any theaters are open--''



``They are,'' Tattletale said.



``--And I couldn't go even if they were.  My face is plastered all over the news, and I've got a tinker who might be watching every computer system and surveillance camera in the city, because she's not willing to go against her bosses.  I can't go shopping, can't leave my territory unless I'm in costume and ready for a fight.''



``More time to go after them,'' Regent said.  ``You can't let this slide.''



``I'm not planning to,'' I said, standing from my seat.



``Hold on,'' Grue said, as my hand came free of his grip.



``Walk with me,'' I said.  ``All of you.  The city may be getting better, but there shouldn't be lights on in this building, and it's only a matter of time before one of the local heroes decides to stop by and see why.''



``We can take them,'' Rachel said, from the rear of the group.



``We can, and we will,'' I said, entering the stairwell.  ``On our terms, not theirs.''



``There's enough enemies to fight,'' Parian said.  She had to hurry around the table to catch up.  ``We don't need more.''



``I agree,'' Grue said.  ``Not that I don't understand the need for \emph{some }response, but you're talking aggression.''



``I'm feeling aggressive,'' I said.  ``I think.  I don't know.  Hard to pin it all down.''



``Might be better to wait until you have a better idea of what you're feeling,'' Grue said.



``It doesn't matter,'' I said, stepping down onto the staircase.  ``Logically, there's no choice but to act on this.  You heard Valefor.  The villain community won't respect us until we answer the PRT, and the so-called good guys won't have a reason to think twice about doing it again.''



``The rest of us aren't as vulnerable as you are,'' Regent said.  ``Don't want to sound disrespectful or anything, but we don't have the same kinds of civilian lives to protect.''



``There're others,'' I said.  ``Part of the reason we uphold these rules is because it sets precedents.  Other villains hold to the rules and we benefit, the opposite is true.''



``The flip side of it,'' Tattletale said, ``Is that we're risking an escalation in conflict.''



``I don't see how they can escalate,'' I said.  ``As I see it, they played the last card they have.  The harder we hit them now, the more clear it is to outsiders that the PRT doesn't have an answer.  I can show that it doesn't bother me, and the effect is the same.''



``Doesn't it, though?'' Tattletale asked.  ``Doesn't it bother you?''



``Yes,'' I said.  ``In terms of \emph{me}, I don't know.  I can't say for sure whether it's justified or not.  But they went after my dad.''



``I get that,'' Grue said, ``I'd be pissed if they went after Aisha.  God, you know, when I was swallowed up by Echidna, and she was filling my head with all the worst stuff I could think of, revised memories, it--''



He stopped, and I paused to glance back up the stairs at him.



``Bro?'' Aisha asked.



He took a second to compose himself, then said, ``I get what you're saying, Taylor.  Believe me.  I was buried in it.  If anyone here knows what it's like to want to protect people--''



``That's not it,'' I cut him off.



``No?''



``It's not about me wanting to protect my dad from the aftermath of all of this.  That's done, and right now he's hurting more than he has since my mom died.  Some of that's on me, and some of it's on the people who sent Defiant and Dragon into the fray.  The damage is done.''



``And you want to go after the non-capes who made the call?''



``Yeah,'' I said.  ``I'm sick of being on the defensive.  I hate waiting for the other shoe to drop, because there's always another shoe, and always a bigger threat.  Speaking of, what's your interpretation on the company we had tonight, Tattletale?  How do you think they're going to play this?''



``The Ambassadors are on the up and up, as far as I can guess their direction.  Accord's unpredictable, which is kind of ironic.  I'd say they're lower priority.''



``They're going to stick to the deal?''



``Until Accord's neurosis pushes him to break it,'' Tattletale said.



``Then who's a higher priority?  The Teeth?''



``Lots of aggressive powers.  Butcher's at the forefront of it all.  Spree has rapid fire duplicate generation, Vex has the ability to fill empty spaces with small, razor-sharp forcefields, Hemorrhagia is a limited hemokinetic with some personal biokinesis, Animos can transform for limited times and packs a power nullification ranged attack while in his other shape.  There's two or three others.''



``I'm asking about their goals,'' I said.  ``Any clue what they're thinking?  Are they going to come after us?''



``Probably.  We seem weak and unbalanced right now, especially with Parian not doing the absolute best job protecting her territory.''



``I'm \emph{trying},'' Parian said.



``You'd be doing better if you'd accept help,'' Tattletale retorted.  ``Except you don't want to do that because you haven't committed to this.''



``I will.  I'm still figuring out the more basic stuff you guys figured out ages ago.''



``Commitment on a mental level, P.  That's more than just coming to meetings.  You don't have to \emph{like} us, but respect us, get to know us, trust us and maybe allow for the occasional intimate moment.''



Parian snapped her head around to stare at Tattletale, in a way that was rather more dramatic than the statement warranted.



``Not \emph{that} kind of intimate.  Sorry hon.  Trust me when I say we're all pretty accepting here, and there's no reason to lie; none of us girls here bat for the other team.''



``I didn't say anything.''



``Of course,'' Tattletale said, smiling.  ``But I was talking about letting us see more of the girl behind the mask.  Share those vulnerabilities, let us give you a shoulder to cry on.''



``I don't need one,'' Parian said, ``And that has nothing to do with me defending my territory.''



``More than you think,'' Tattletale said.  She glanced at me, ``They're the type to prey on weakness, and Parian's capable of only protecting a short section of her perimeter.''



``Hire people?'' I asked.  ``Henchmen, mercenaries.''



``I don't want to put innocents in the line of fire,'' Parian said.



``You don't want others to suffer if the Teeth come after the people you wanted to protect, either,'' I said.



``I don't know what you want me to do.  If I call for help, they'll retreat, and we wind up wasting \emph{your} time, while leaving me looking and feeling useless.''



``There's an alternative,'' I said.



``What?''



``What I was talking about before.  Going on the offensive.  Only it's not about just the good guys.  I'm talking about targeting our enemies, wiping them out \emph{before} they hurt us and give us cause.''



``That's dangerous,'' Grue said.



``You guys keep saying things along those lines,'' I responded.  ``I shouldn't be so strict with our enemies, I shouldn't ratchet up my involvement in things, I shouldn't be aggressive.  It's \emph{more dangerous} to leave them loose, to always give our enemies the first move.''



``The flip side to that coin is that it gives everyone \emph{else} we deal with less reason to play ball.  We need to get other villains to parley if we're going to seriously hold this territory.  The Ambassadors are only step one,'' Grue said.  ``If some other group comes into town and they're considering joining us, are they going to look at whatever humiliating defeat we visit on the Fallen and feel it's better to attack \emph{us} first?''



``Escalation,'' Parian echoed Tattletale's earlier statement.



I sighed.  Atlas had descended from his vantage point above the building, and flew in to land next to me.  I ran my hand along his horn.



``We're not\ldots the idea here isn't to \emph{attack} you, Taylor,'' Tattletale said.  ``Hell, what they did was \emph{low}.  You said it yourself, in that cafeteria.  But you're talking about changing our dynamic, and it's a dynamic that's been working.  We've already been through some high-tension, high-conflict scenarios.  A bunch of times when we went \emph{days} without a chance to breathe.  You want to ratchet that \emph{up}?''



``Not entirely,'' I said.  ``If we do this right, if we play this smart, then this should reduce the amount of conflict.  I need to know if you guys are on board.''



``Yeah,'' Rachel said.



``I'm in,'' Regent replied.  Imp nodded.



``My- my vote doesn't count,'' Parian said.  ``I only wanted a show of force, to see if we couldn't scare the Teeth.  Only I think it had the opposite effect, because what you guys were saying about Butcher is spooking me.  If you guys want to help me with them, okay.  But I don't want to commit to anything major here, and I can't tell you guys how to operate, because I'm new to this.  Skip my vote.''



``Okay,'' I said.  ``Tattletale?  Grue?''



``I've already said my bit,'' Tattletale said.  ``You call the shots in the field, and act as the face of the group, I do the behind the scenes stuff.  That's how we worked it out.  I'm kosher with that.''



Grue said, ``I have one thing to say.  Think it over, or keep it in mind.  We made it further than most groups do.  Some villains set their sights high, and they fall.  Others try to eliminate their enemies and get eliminated in turn.  Still others set their mind on a goal and they strive for it, only to get worn down along the way.''



He paused, glancing away.  I didn't interrupt.  Picking the right words?  Thinking about himself, as one of the ones who were worn down by circumstance?  Or maybe he was thinking about \emph{me} in that light.



``Maybe part of the reason we made it this far was because you weren't striving for that.  When we were villains, you were trying to be the good guy, behind the scenes.  When we were trying to take out some pretty nightmarish opponents, your focus was on surviving more than it was on attacking.  I didn't get the impression you craved to be team leader or to rule the city, but you took on the job because you knew the alternative would be disaster.''



I nodded.  Even if I'd wanted to say something in response, I wasn't sure what I would've wanted to say.



``Maybe the reason I'm less comfortable with this is that it's not your usual pattern.  I feel like you're wanting to be aggressive because you're hurt and angry.  There's nothing to temper it.  Think about it, okay?  I won't tell you not to do this.  Despite everything I just said, I do trust your instincts, and I'm not sure I trust mine these days.''



``Grue--''



``I \emph{don't}.  That's me being honest.  Do what you have to do, but do it with your eyes wide open.''



``Okay,'' I said.  ``I'll try.''



I had a sudden impulse to hug him, to hold him as close and as tight as our costumes allowed, my arms tight around his broad back, his muscled arms holding me just as tight.



The idea alone made me feel like I might suddenly burst into tears, and I found it startling, inexplicable.



I didn't hug Grue; I wasn't sure enough about what I was feeling or why, didn't want to come across as anything but a leader.  Leading this team was something I could do.  Something concrete, with real dividends.



Why had I brought Atlas here?  Had I already been thinking about running?  Avoiding further contact with these guys?  Avoiding Grue?  It was disconcerting to think about.



Tattletale was staring at me.  Could she read what I was experiencing, or get a sense of the emotions that were warring inside me?



``Okay,'' I said, and I was surprised at how normal I felt.  ``We're playing this much like we did against the Nine, only we aren't waiting for better excuses to do it.  Groups of three, one group active at a time, one target at a time.''



``Who are we fighting?'' Rachel asked.



``The Fallen, the PRT, and the Teeth.''



``And you're in this group of three for tonight's mission?'' Tattletale asked.



``Yeah.''  I needed a release, to do \emph{something}.



She glanced at Grue, and I suspected there was some kind of unspoken agreement there.  She met my eyes, or the opaque yellow lenses that covered my eyes.  ``I'll come.''



``You're ops,'' I said, ``I thought the whole point of that was that you'd stay behind the scenes and out of trouble.''



``I'll come,'' she repeated herself.  No argument, no manipulation.  Only the statement.



I sighed.



``Me too,'' Rachel said.



``Not sure that's a good idea,'' Tattletale said.  ``Maybe someone more subtle?''



``No,'' I said.  ``It's fine.''



Subtlety wasn't what I had in mind.



\sectionbreak



Bentley crashed into the side of the PRT van.  The vehicle rocked, but it was set up to be in the field amid villains with superstrength and literally earth-shattering powers.  It didn't tip over.



Two more dogs crashed into the side of it, and the thing fell.  The PRT officer in body armor fell from the turret at the top, his armor absorbing just enough of the impact that he wasn't badly hurt.



The containment foam sprayers might have been an issue, but none of the uniforms were in a position to use the stuff.  I'd come prepared, and each sprayer was either thoroughly snagged on spider silk at the top of the equipped trucks, or the PRT agents who were wearing the portable tanks were bound, blind and under siege by massed bugs.



Dovetail flew after Atlas and I, a trail of luminous slivers of light falling in her wake.  She was good at maneuvering in such a way that the sparks didn't fall on the PRT uniforms and heroes below, even with my swarm crawling over her head, shoulders and arms.  Where the slivers touched something solid, they ballooned out into what Tattletale had described as soft force fields, encasing the subject.  Anyone could push hard enough against the force fields to break them, even with multiple fields layered over one another, but it impeded movement, and she could hover over a target to keep reinforcing the forcefields until the victim could be smothered in more permanent containment foam.



It might have been a crummy power, but she was \emph{fast}.  If she could have thrown the forcefield-generating slivers further than she did when she flung her arms out, she might have had us.



It was to my advantage that it was easier to dodge pursuit than to match someone else's course exactly.



Didn't hurt that she had bugs in her nose, ears and mouth, and that she was being bound by silk, limiting her range of movement with every passing second.  She was already unable to use the compact containment foam sprayer she had built into her costume.  Nothing I did would stop her from flying, but so long as she was blind and unable to use her arms, I didn't see her being too much of a threat.



She wasn't making headway on the offense, but retreating wouldn't change her circumstances.  I'd still bind her in silk, blind and choke her.  Her costume had a flared collar, and my bugs were crawling inside, between skin and cloth.  That attack was as much about the psychological effect as about getting to more skin to inflict bites.



I wasn't sure if it was just me, but her movements were bordering on the frantic, now.



No holding back.  I only had so many wasps and hornets, but I did what I could.  Mosquitoes were a good one.  Welts.  Leaving a mark.



Rachel's dogs knocked over another one of the vans that had been circled around the PRT headquarters. The van was knocked into the side of the building, bending the bars that were supposed to protect the windows.  Each window cracked, with the lines spiderwebbing out between the hexagonal sections, but they didn't break.



Adamant got into close quarters combat with the dog, slashing at it with pieces of his armor and driving the animal back.



Rachel whistled, shrill, and two dogs tackled him.  He delivered one good swipe before the other blindsided him.  The disadvantage of forming a full covering of armor was that it limited his peripheral vision.



She wasn't going even two seconds without giving a command.  There were five dogs in the field, or four dogs and one young wolf, and many were lacking in serious training, so she managed them with lengths of chain between their collars and Bentley's, and by giving enough commands that they wouldn't have time to get creative and go after one of the PRT uniforms.



Sere was indoors, along with Triumph.  Binding Sere had been a first priority, and I'd achieved it in much the same way.  He'd done what he could to target the bugs managing the threads, and to disentangle himself, but time spent on that was time he wasn't moving outdoors and shooting me or one of the dogs.  As with Dovetail, I'd managed to make enough progress that he was more or less out of the fight.  She was blind, he was immobile.



The other heroes would be arriving soon.  I double-checked Dovetail wasn't in a position to give pursuit, then ventured inside, entering through an open window on the uppermost floor.



I felt calm, which was odd, given the scene.  Bugs swarmed every employee, from the official heroes to the kids who might have been interns.  Some howled in pain, others screamed more out of fear, or yelped as bugs periodically bit them.



The bugs gave me a sense of the route I needed to take, my destination.  There were offices in the back corner, but I had a sense of where I was going.  I'd been here before, when Piggot had been director.



I saw the labels on the door.  Commissioner.  Deputy Director.  Director.



I opened the last door.  Director Tagg.



He held a gun, but he didn't point it my way.  There was a woman behind him, using him as a shield.



I'd had statements ready, angry remarks, any number of things I could have said to him, to punctuate what my swarm was doing to his assembled employees.  Statements, maybe, that could have surprised him, woken him up to what he'd done to me.



Then I saw the steel in his eyes, the sheer confidence with which he stood in front of the woman\ldots they had matching wedding bands.  His wife.  I knew in an instant that there wouldn't be any satisfaction to be had that way.



Rather, the word that left my mouth was a quiet, ``Why?''



His eyes studied me, as though he were making an assessment.  His words were gruff, the gravelly burr of a long time smoker.  He very deliberately set the gun down on the desk, then replied, ``You're the enemy.''



I paused, then pulled off my mask.  I was sweating lightly, and my hair was damp around the hairline.  The world was tinted slightly blue in a contrast to the coloring of my lenses.  ``It's not that simple.''



``Has to be.  The ones at the top handle the compromising.  They assess where the boundaries need to be broken down, which threats are grave enough.  \emph{My} job is to get the criminals off the streets and out of the cities.''



``By starting fights in schools.''



``Didn't know it was a school until the capes were already landing,'' he replied.  ``Had to choose, either we let you go, and you were keeping an eye out for trouble from then on, or we push the advantage.''



``Putting kids at risk?''



``Dragon and Defiant both assured me you wouldn't risk the students.''



I sighed.  \emph{Probably right}.



Someone behind me screamed as a group of my hornets flew to him to deliver a series of bites across his face.



``Barbaric,'' Director Tagg said.



``Inflicting pain isn't the point.''



``Seem to be doing a good job of it,'' he commented.



``There are heroes on their way back from patrol, your guys called them in.  But there's also news teams on the way here.  \emph{We} called those guys in.  They'll find your employees covered in welts, every PRT van damaged or trashed.  Your employees won't be able to get any cars out of the parking lot, so they'll have to walk, which will make for some photo opportunities.  A handful of heroes will be a bit the worse for wear.  You can try running damage control, but some of it's bound to hit the news.''



``Uh huh,'' he said.



``I couldn't let you get off without a response from us.''



``Didn't expect you to.''



``This was as mild as I could go,'' I said.  ``I think you know that.  I'm not looking to one-up you or perpetuate a feud.  I'm doing what I have to, part of the game.''



``Game?  Little girl, this is a \emph{war.}''  His voice took on a hard edge.



I stopped to contemplate that.  Rachel was destroying the last containment van, and Tattletale was saying something to her about incoming heroes.  I was low on time.



``If it is a war, my side's winning,'' I said.



``And the world's worse off for it.  You can't win forever,'' he said.



I didn't have a response to that.



He must have sensed he had some leverage there.  ``All of this goes someplace.  Do you really see yourself making it five more years without being killed or put in prison?''



``I haven't really thought about it.''



``I have.  Bad publicity fades with time.  So do welts and scabs.  Five or ten years from now, provided the world makes it that long, nobody will remember anything except the fact that we fought back.  Good publicity will overwrite the bad, carefully chosen words and some favors called in with people in the media will help whitewash any of our mistakes.  We're an \emph{institution}.''



``So you think you automatically win?  Or you're guaranteed to win in the long run?''



``No.  They didn't pick me to head this city's PRT division because I'm a winner, \emph{Ms. Taylor}.  They picked me because I'm a scrapper.  I'm a survivor.  I'm the type that's content to get the shit kicked out of me, so long as I give the other guy a bloody nose.  I'm a stubborn motherfucker, I won't be intimidated, and I won't give up.  The last few Directors in Brockton Bay met a bad end, but I'm here to stay.''



``You hope.''



``I \emph{know}.  You want to fight this system?  I'll make sure it fights back.''



``So you want to escalate this?  Despite what I said before?''



``Not my style.  I'm thinking more about \emph{pressure}.  I could pull your dad in for questioning every time you pull something, for example.  Doesn't matter where, doesn't matter who it's directed at.  You or your team do anything that gets an iota of attention, I drag the man into the building, and grill him for a few hours at a time.''



I felt a knot in my stomach.  ``That's harassment.''



I was aware of Tattletale approaching me from behind.  She leaned against the doorframe, arms folded.



``It's a war of attrition,'' Tagg said.  ``I'll find the cracks, I'll wear down and break each of you.  If you're lucky, then five years from now they'll remember your names, speaking them in the same breath as they talk about the kid villains who were dumb enough to think they could keep a city for themselves.''



``He's playing you,'' Tattletale murmured.  ``He knows he's got you on a bad day.  Best to just walk away.  Remember, the Protectorate hasn't had a good day against us yet.''



I thought about asking him about Dinah, but there wasn't a point.  It was something he could use against me, and I already knew the answer.



I approached the desk and turned around the photo frames.  The second showed Tagg with his wife and two young women.  A family portrait.



``You have daughters,'' I said.



``Two, going to universities halfway across the world.''



``And you don't feel an iota of remorse for hurting a father through his daughter?''



``Not one,'' he replied, staring me in the eye.  ``I look at you, and I don't see a kid, I don't see a misunderstood hero, a girl, a daughter or any of that.  You're a \emph{thug}, Taylor Hebert.''



\emph{A thug}.



His mindset was all `us versus them'.  Good guys versus the bad.



It wasn't much, but it served to confirm the conclusion I'd already come to.  Dinah had volunteered the information.  Whatever else Director Tagg was, he wasn't the type to abuse a girl who'd been through what Dinah had.



``We should go,'' Tattletale said.  ``Rachel's downstairs with all her dogs, we can run before the reinforcements collapse in on us.''



``Yeah,'' I said.  ``Nearly done.  You, back there.  Are you Mrs. Tagg?''



The woman stepped a little to one side, out from behind her husband.  ``I am.''



``Visiting him for the night?''



``Brought him and his men donuts and coffee.  They've been working hard.''



``Okay,'' I said.  ``And you stand by your husband?  You buy this rhetoric?''



She set her jaw.  ``Yes.  Absolutely.''



I didn't waste an instant.  Every spare bug I had flowed into the room, leaving Director Tagg untouched, while the bugs flowed over the woman en masse.  She screamed.



He reached for his gun on the desk, and I pulled my hand back.  The thread that I'd tied between the trigger guard and my finger yanked the weapon to me.  I stopped it from falling off the desk by putting my hand on top of the weapon.



Tagg was already reaching for a revolver at his ankle.



``Stop,'' I said.



He did.  Slowly, he straightened.



``I'm illustrating a point,'' I said.



My bugs drifted away from Mrs. Tagg.  She was uninjured, without a welt or blemish.  She backed into the corner as the bugs loomed between her and her husband.



``Not sure why.  Doesn't change my mind in the slightest,'' Tagg said.



I didn't respond.  The swarm shifted locations and dogpiled him.  Stubborn as he professed to be, he started screaming quickly enough.



I picked up the gun from the edge of the desk, joining Tattletale.  We marched for the exit together, moving at a speed between a walk and a jog, passing by twenty or so PRT employees, each covered in bugs, roaring and squealing their pain and fear to the world as they stumbled blindly and thrashed in futile attempts to fight the bugs off.



Nothing venomous, the wasps and hornets weren't contracting their bodies to squeeze the venom sacs.  There was nothing that could put their lives at risk.  It was still dramatic enough.



``He's right,'' Tattletale commented.



``About?''



``You won't change his mind with a gesture like that.  Sparing his wife.''



``Okay,'' I replied.  I opened a drawer and put Director Tagg's service weapon inside, while Atlas ferried Tattletale down to the ground floor.



Atlas returned to me, and I took to the air, flying just above Lisa and Rachel and the dogs as we fled the scene.  I made a point of leaving every single bug inside the PRT headquarters, to infest it until they had the place exterminated, which would only be another photo opportunity for the media, or to serve as a perpetual reminder as it took weeks and months for all of the bugs to be cleared out.



The news teams were already arriving on the scene.  No doubt there was a camera following us.  I remembered Director Tagg's threat, to bring my father into custody.  Only a threat, going by his wording, but it did make me think about how every activity, every thing I did that brought me into the public consciousness, it would be a little twist of the knife that I'd planted in my dad's back.



Not a good feeling.



Maybe the little demonstration I'd done with Tagg's wife hadn't been for him.  It could just as easily have been me trying to prove something to myself.





