





Atlas started to falter.  Compared to humans and other animals, bugs didn't quite have the same ability to push themselves past the breaking point.  Most bugs were small, and their bodies were hyperefficient, condensed down to the essential elements.  If a bug needed to be able to leap, to lunge or to fly, it maintained a certain capacity and it didn't generally go beyond that.  It wasn't absolute, but I'd found it was a definite trend.



In brief, there wasn't really a hundred-and-ten-percent.  When Atlas started demonstrating fatigue and difficulty in carrying me, I wasted no time in setting him down on the ground.



I ran my hand along the giant beetle's shell while Tattletale and Rachel caught up.



``Problem?'' Tattletale asked.



``No,'' I said.  ``Yes.  Can I catch a ride on a dog?''



``Yeah,'' Rachel said.  She whistled, loud and sharp enough that I flinched, and swept her finger in my direction.  One of her dogs took the cue and approached me.



``What's wrong with Atlas?'' Tattletale asked.



``He's wearing out,'' I said.  My voice sounded flat.  ``During the Echidna fight, I saw how quickly he was getting tired, and I chalked it up to the fact that he hadn't eaten properly while separated from me\ldots but I've been realizing that it's more than that.  I haven't figured out the perfect diet to give him absolutely everything he needs, and I'm only barely managing to maintain an equilibrium.  Every time he gets hurt, every time he gets tired, there's general wear and tear I can't compensate for.''



``I'm sorry,'' Tattletale said.



``That's the way things go, isn't it?  Nothing works a hundred percent right.''



``I suppose you're right,'' she said.  ``I have to wonder, when you named him, what was the idea behind calling him \emph{Atlas}?''



``My mom raised me as a reader,'' I said.  ``He's a giant-sized Hercules beetle, and the only name-upgrade I could think of from Hercules was the titan Atlas.''



``The titan who bears the weight of the world on his shoulders.  Apropos.''



I shrugged.



``And like his master, he's having trouble with his burden?''



``I'm really not in the mood for the Tattletale psychoanalysis.''  I climbed onto the dog's back.  It wasn't one I knew well, and moved away from me as I climbed up its side, making the process more awkward.  Rachel made sound that was almost a bark, almost an `ah!', and the animal went still.



``Maybe it's not exactly what you want, but what if it can help?''  Tattletale asked.



``My issues aren't ones that can be fixed with words,'' I said.  ``Unless you have any insights to offer about Tagg, a way to make this world suddenly make sense, or a way to make people stop being such \emph{assholes}, such \emph{morons}, then I'm not sure I want to hear it.''



``He got to you.''



``No,'' I said, shaking my head.  ``Nothing he said--''



``But he got to you, even if you ignore everything he said.''



``Armsmaster,'' I said.  ``Kaiser.  Purity.  Miss Militia.  Piggot.  Dragon\ldots a bunch of others I can't even be bothered to think of.  Why is it so hard to find someone who's willing to \emph{cooperate}?  To find someone that's on the same page as me?  They keep making these calls I just can't understand, sometimes unfathomable, \emph{stupid} calls, and things keep falling apart.''



``They probably look at you and wonder why you can't fall in line with \emph{their} perception of the way things should go.''



I shook my head.  ``It's not like that.''



Tattletale didn't interject or argue.



I struggled to find the words.  ``\ldots{}What I'm talking about, ideas like keeping the peace, keeping people safe, making sure that everyone's safe, it's\ldots they're not complicated.  This is basic stuff.  If we can't get the \emph{fundamentals }right, then how are we supposed to handle the more complicated stuff, like keeping this city running, or stopping war from breaking out?''



``If we could all handle the fundamental stuff, the larger issues wouldn't exist.''



``No, he\ldots there's no way it makes any sense, whether you're talking fundamentals or larger scale.  He attacked a school to, how did he say it, to give me a bloody nose?''



``It's probably more complicated than that.  You know as well as anyone that we put on a mask and play a role when dealing with our enemies.  He was playing up a certain attitude because he knew it was the only way to get to you.''



``Why did he have to `get to me'?''



``You attacked him.''



``I mean, why did it even have to get to that point?  They weren't as aggressive with Kaiser and Purity, when unpowered members of Empire Eighty-Eight were dragging people from their homes.  They didn't act on this scale when the ABB was dealing in hard drugs and ambushing people on the street to tell them that because of where their parents were born, that they had to be soldiers, prostitutes or pay money every month in tribute.  They were doing that to \emph{middle schoolers}.''



``You took over a city.''



``How is that worse?  How does that even compare to those other guys?''



``It doesn't compare,'' Tattletale said.  She hopped down from Bentley's back.  She paced between Rachel and I, thumbs hooked into her belt.  Rachel stared at me, her expression unreadable, her mask dangling around her neck by a strap.  Tattletale continued, ``Not really.  But it means a world of difference to them.  They have to care about appearances.''



``Maintaining appearances is so important that they have to attack a school?  Break the unwritten rules?''



``I could go on a whole spiel about the unwritten rules.  But that's not important.  For people like Tagg and Piggot, it's cape business, and they're not quite part of that.  And yeah, appearances are worth putting kids at risk, for what they're facing.  Things are just calming down here--''



Rachel snorted.



``--But they're only picking up for the PRT.  They're running scared, hemorrhaging members.  They're falling apart, and they're big enough in the grand scheme of things that we don't even know the repercussions if this keeps going on.  Every team that fights the Endbringers relies on the Protectorate for information, for backup, equipment and even periodic training.  But even beyond that, beyond the capes, there are hundreds of millions of people around the world who are watching the Protectorate, looking to them for reassurance.  Our perspectives and feelings are barely a factor in the face of those hundreds of millions of watching eyes.''



\emph{``}Barely a factor.''



Tattletale shrugged.  ``They put on a brave face, they put a tenacious fucker in office here, and they gear up to take a bite out of us.  They don't want to \emph{win. } Not completely, not all at once.\emph{  }They \emph{need} us, because they don't have the capes to dedicate to protecting this territory, not even with the possibility that the portal becomes something big.  They aim to take you out, destabilize us, and maybe then they hope to focus on the \emph{other} bad guys.  The Teeth, the Fallen, anyone else who shows up and doesn't play by the rules.  They do something to assure the world that they're still relevant, and they keep the balance, all with a minimum of resources expended.''



``And in doing that, they fuck with the rules, and they attack a high school.''



``Are you really surprised that they broke the rules?  \emph{We} have, \emph{Piggot} did, when she wanted to drop bombs on us while letting us act as decoys for bigger threats.  The rules are only useful so long as they protect the status quo, and Brockton Bay bent the status quo over backwards and fucked it a \emph{long} time ago.''



``And the school?''



``Dinah,'' she said.  ``They had some basic, hard numbers saying that you wouldn't do something disastrous, and they have PR to clean up the mess afterwards.  I suspect there'll be something in the news early tomorrow.  They'll say you were an undeniable threat, they'll twist things around, fudge the truth or outright lie, and they'll suppress anything that contradicts that line.  After \emph{that}, they'll have Tagg and the local heroes keep looking to take a bite out of us, do some damage \emph{they} can put on camera, for the benefit of the hundreds of millions of watching eyes, and they'll keep at us until they do.  He was being honest about that much.''



I clenched my fist.  I didn't want to think about Dinah.



``Sorry,'' she said.  ``But it's better you know this in advance, so it doesn't blindside you when the news--''



``Rachel,'' I interrupted Tattletale.



``What?''  Rachel asked.  Her eyes hadn't left me.



``Can I borrow this dog?  I'll look after him.''



``He needs to eat.  Can you get him back to me by tomorrow morning?''



``I asked Tattletale to ship dog food to every headquarters, the same kinds you feed your dogs, just in case,'' I said.  ``Not tomorrow morning, but I'll make sure he eats.''



Tattletale frowned, ``Skitter, we need to talk about--''



``I got the gist of it,'' I said.  ``Did you ship the food?''



``Yes.''



I looked to Rachel, ``I'll walk him, make sure he has food and water.''



``No need for a walk,'' Rachel said.  ``Boston terriers don't need more than one a day.''



``Okay,'' I said.



``I'll come for him tomorrow afternoon,'' she said.  As an afterthought, she said, ``His name is Radley.''



``Thank you,'' I said.



No questions, no pressure, no explanations.  It was just Rachel, stepping outside of her comfort zone and trusting one of her dogs to someone.  It helped more than everything Tattletale had said put together.



Not that \emph{that} was saying much.



``Let's go, Radley.''



Radley hesitated to obey.  I half-expected Rachel to urge him forward, but she didn't say a thing, apparently content to let me take charge.



I was glad when he started running, glad on so many levels.



\emph{Moving} felt good.  It wasn't me running, my feet pounding on the ground, but feeling Radley's muscles shift beneath me, feeling the impacts of his feet on the ground, jolting through my body to the point that I had to clench my teeth to keep from biting my tongue, it was good.



I'd always liked the sensation of the wind in my hair.  It was cleansing, soothing, if not \emph{relaxing}.  It was cool, when the air around me was warm and humid.



I shifted position, holding on with only one hand, and pulled off my mask with the other. The world was blurry, I didn't have the extra hand to don my glasses, but I could feel the wind in my face now.  I shut my eyes, trusting to Radley and my swarm-sense to navigate the streets.



But where was I supposed to go?



I wanted to see Dinah, knew it was the last place I should go.  I already knew the answers, already knew that the conclusion was a foregone one.  Didn't want to think about it, just like I didn't want to think about those two pieces of paper she'd left in the car before we'd parted ways.  I was actively trying \emph{not} to think about them, as a matter of fact.



Dinah had left me two messages, and I had little doubt that she'd done it that way for a reason.  To meet her now, it would go against that, it would put me in the heroes' sights,  and it would crystallize things I didn't even want to think about into a single discussion.



My dad?  No.  There was nothing to say, no signal that would work.  If he was even there, I wasn't sure I wanted to see the media around his place, or the Protectorate, the reminder that I hadn't just abandoned him, but that my very existence was inconveniencing him.



I steered Radley around a corner, hauling on one of the chains.  I wasn't really strong enough to make him turn his head, but Rachel had trained him to respond to slight cues, and it seemed his personality was more cooperative than not.  If he'd been stubborn, he could have chosen to run up until Bitch's power wore off.  Not that I really minded.



``Good boy,'' I said.



What was I supposed to do?  I didn't have any hobbies.  For one and a half years, I'd just been trying to get by, managing with school, reading, surfing the web aimlessly.  Once my powers had manifested, my hobby had been preparing for the idea that I'd go out as a superhero.  I'd had only \emph{this} and my day-to-day life as Taylor since then, and only one of those things had survived the day.



We ran with no destination, until Radley had foam flecking the corner of his mouth, and the meat of his back started shifting position in a way that suggested he was shrinking.



At my instruction, Radley slowed to a walk, then a complete stop.  I slid off his back.  Holding the chain, I led him in a walk.  It served to help me work the kinks out of my arms and legs, and it let Radley cool down after the run, flesh sloughing away around him.  Atlas followed, flying above us.



I wanted to see Brian, didn't want to continue our discussion from earlier.



I itched to deal with one of my enemies, to ride off to battle and do \emph{something} about the Teeth or the Fallen, but I didn't trust that I'd be focused enough to tackle the situation and fight at my best.



I couldn't imagine I'd be focused after a good night's sleep, either.



Radley couldn't walk any more, and I waited while the last of his body sloughed away, gathering up the chains.  It made for a surprising amount of weight, especially when it was all coiled up into a single length.



One chain had a collar on it.  I found Radley's real body in the fluid-filled sac that  encased him, and punctured it to get my hands on him.  I managed to attach the collar, and clipped one end of a chain to it.  I gave Atlas some of the chain, and lifted the remainder over my head, shouldering the burden.



Without Atlas or Radley to carry me, I faced a long walk, even if I wasn't sure where I wanted to go.



Time to think, without any outside forces to interject.



Damn Tagg.  I hated that my conversation with him was among the most recent, the one that I couldn't help but dwell on.



Where the hell had Radley and I even gone?  What was even close by, here?  Captain's hill?  The woods?  The upper end of Grue's territory?  What would even motivate me to come this way?



I kept walking.  Part of it was that I couldn't bring myself to go back to my territory, to answer the questions of my underlings.  Another part of it was that I knew I'd wake up after a fitful night's sleep, and I would resume being Skitter.  I would be \emph{Skitter} with anyone and everyone I interacted with for a long time.



My confused thoughts crystallized into a realization when I found a short stone wall topped by an iron grille railing, sharp points spearing toward the sky, protecting the inhabitants of the property.



I scooped up Radley with one arm and scaled the wall.



The ground was soft, thick with bugs.  The area was dense with trees, once young, now overgrown.  The air was cooler here, thanks to the shade the trees had offered during the day and the wind that blew down from the surrounding hills.



I took a seat on the grass.



``Oh boy,'' I said, ``Where do I even begin?''



Radley seemed to think I was talking to him.  He approached and nudged me with his nose.  I scratched behind his ears, gently.  I'd altered the armor of my gloves, and they ended more in points.  Radley seemed to like it, pushing against my fingertips, his eyes half-closing.



``I guess I should say I'm sorry it's been so long, mom,'' I said, still scratching Radley.



The headstone, naturally, didn't respond.  There were only the words:



Annette Rose Hebert1969-2008
She taught something precious to each of us.



``It's\ldots it's sort of humiliating, to think about everything in context.  I get this knot in my chest, right up near my collarbone, when I think about getting into everything, about filling you in and catching you up on the past few months.  It's almost harder than it'd be to explain to dad, and I never even managed to do that.''



Silence lingered.  We were remote enough that there weren't even the sounds of the city.  Oblivion, as clean as it might be in Grue's darkness.



``I guess things have kind of turned upside down.  That whole superhero thing I told you about, before?  It\ldots really didn't work out.''



I laughed a little, a small sound, humorless.



Radley climbed into my lap and turned around until he was nestled in place.



``And it's like\ldots if I even started to tell you everything that went on, all of the stuff that dad's probably finding out about?  Stuff maybe \emph{worse} than what I was saying to intimidate Dragon and Defiant, on the cell phone videos that made it to the news?  I don't think I could manage it.  It's- how did I even get to this point?  I did horrible things, stuff that makes me feel three feet tall when I just \emph{imagine }telling you or dad about it, and the stupid thing is I'm not sure what I would've done different if I had to do it all over again.



``So where do I begin?  How do I even frame it all?  Everything's flipped around.  I'm not alone anymore.  I have maybe a hundred and fifty people working for me, some people who trust me with their lives, others who owe me their lives.  I've got Lisa and Brian.  Rachel.  There's Alec and Aisha too, but I'm not as close to them.  We've, uh, we've been through a lot.  Life and death stuff.  On television, in the movies and in books, you sort of get the impression that you make it past the one big hurdle, and you're bound together by circumstance.  It happened a lot in the books you read to me at night.  Not so much in reality.



``Except getting through the crisis doesn't mean we're all together forever, without our issues.  We're close.  We're \emph{closer}, in the aftermath of it all, but I'm not sure where Brian and I stand.  Right now, when I'm maybe feeling lower than I have in forever, I don't even feel like I can talk to them.''



My swarm detected someone traveling the grounds.  I glanced over in that direction, saw the dim glow of a flashlight.  It didn't turn my way, and in a minute, he was gone.  A caretaker of the grounds.  Groundskeeper?  Whichever.



``Brian wants to address the problem, Lisa wants to understand it.  I'd go to Rachel, \emph{will} probably go to Rachel, but I don't know that I can really talk about any of this with her.  I don't know if she has any real conception of what I lost, today.  I don't want to suggest you're the last person I'd turn to, but I think the real reason I came here was because I wasn't sure where else to go, to have someone to listen.''



I sighed.  Radley echoed me, doing the same, supine in my lap, eyes closed.



``Um.  I've gone from an insignificant nobody to someone that's being talked about all over the world.  I didn't even really mean to, but I kind of wound up taking over a city.  It needed doing, so I did it, and we can't give up the job because others would step in to take over, and they wouldn't be as fair to the locals, I don't think.  Tattle- Lisa was saying she thinks the authorities are holding back because they need us here.  They don't like us, they don't like \emph{me}, but we're a fixture, now.  So here I am, and governments on the other side of the planet are probably discussing contingency scenarios and the possibility of bad guys taking over \emph{their} towns.  I'm on the news, and I'm all over the internet, and I guess even your name's come up.  Dad's too.''



I pulled my mask from where I'd tucked it into my belt and turned it over.  I held it up so it was facing the headstone.



``I guess I should get around to saying it outright.  I'm a supervillain.  Crime lord of Brockton Bay.  It's not as bad as it sounds.  Or maybe it's worse.  I've saved lives.  Fought Leviathan, fought the Slaughterhouse Nine and Echidna.  I've also \emph{taken} a life.  Fought the heroes, and hurt people who probably didn't deserve it, just to make a point.''



I had to stop there.  I sighed, then turned to stare out over the unlit graveyard and the city beyond the short walls.



``This whole thing, I didn't really ask for any of it.  I made myself into this\ldots \emph{entity}, just to get by.  I'll probably have to keep doing it.  I tried to avoid hurting people out of anger, but that sounds pretty feeble when I look at what I've done.  A little while back, there was this guy who was dying.  One of the Merchants.  The man had taken a boy away from his sister and did some shitty stuff in general.  Hurt people.  I left him there to die, and part of the reason I did it was because I knew I needed to be \emph{harder}, to reassure myself that I could kill \emph{another} man when the time came.  Which I did.



``I told myself I was doing \emph{that} to save a little girl.  I don't even know why I made it as big a deal as I did.  Saving Dinah.  Some of it might have been because I was trying to do what was \emph{right}, and because I wasn't sure anyone else would be able to do anything about it.  But the more I think on it, the more I think I was trying to make up for the bad stuff I'd already done.''



There were a fresh set of flowers in the small, narrow vase at the base of the headstone.  I picked it up and studied it.  Had my dad paid a visit earlier in the evening?



``She turned on me, you know,'' I said.  ``The girl I saved.  And I think I sort of know why she did it.  I understand the rationale.  I don't even blame her.''



I fished the two little notes from my belt.  I'd crumpled and flattened them out so many times they were little better than tissue paper.  I hadn't wanted to read them, but I hadn't been able to throw them away, either.



``Shit,'' I muttered.  ``What gets me, more than anything, is the injustice of it all.  There's no karmic retribution, no reward for good deeds or punishments for the bad.  It's almost the opposite.  It might explain why the Protectorate's in such rough shape.



``I do horrible things, kill a man, and I can't even bring myself to feel bad about it.  I scared innocents, did property damage, attacked good heroes who were trying to protect the city and the shitty heroes who were doing the job for selfish reasons, and I get rewarded.  Power, prestige, respect.''



I straightened out the notes so they were each flat, being careful not to tear them.



``And I save a girl from the clutches of an evil, scheming crime lord, and \emph{this} is my reward.''



I held out the papers for the tombstone.  Two squares of paper.  Each had a number in the upper left corner, circled, to indicate the order the notes should be read in.  Two words for the first note, two and a half for the second.



1.  Cut ties.



2.  I'm sorry.



``Let me tell you, mom.  If there are two and a half words you don't want to hear from a person who can see the future, those words are `I'm sorry'.  It's terrifying.  She gave me instructions, and I didn't follow them.  I \emph{knew, }I almost did it, several times over, but I didn't make the call.  I didn't leave dad.  So maybe that's why she forced my hand by going to the authorities and telling them to out me.''



I took my time folding up the notes, tucking them into my belt.



``I guess this next bit must be important, if she was willing to do this to me after everything I did for her.  Maybe it's for the greater good.  Maybe it gives me the greatest chance at surviving what comes next.''



I tensed as the groundskeeper with the flashlight appeared again.  The flashlight turned my way, but he didn't seem to notice me.



``She says she's sorry, and it's like\ldots I'm not mad at her.  I don't blame her, because she's just one piece of a bigger picture, and she's a pawn in it all, just like me.  It's \emph{everything} that's fucked up, isn't it?  The whole dynamic where wrongs get rewarded and right gets punished, some of the good guys turning out to be worse than the worst of the bad, the sheer lack of \emph{cooperation}, when there's not just \emph{one} apocalypse coming, but \emph{two}.  The Endbringers and this thing with Jack Slash.''



I sighed.



``I've spent far too much time looking at these notes, wondering why she wrote them, interpreting them, and considering the worst case scenarios.  I've thought about it until I started thinking in circles.  I keep coming back to different facets of the same idea.''



I could imagine her there.  My mom, standing in front of me, a physical presence.  All of her gentleness and warmth.  Her silent, quiet disapproval.  Her brilliance, which she couldn't share with me right now.



I felt a sort of relief.  Being able to talk it out, it helped clarify my thoughts where I'd felt so lost, before.  I was feeling more direction, now.  I could see a goal, something to aim for.  I didn't like it, but I'd known from the moment I read Dinah's notes that I wouldn't like the outcome.



``I've got to be heartless, I think,'' I said, and my voice was barely above a whisper.  I was aware of the groundskeeper approaching, but I didn't move.  ``I know you and dad won't approve of this, but Dinah seems to think I have a bigger role to play in what comes next, and maybe I won't be in the right position, in the right place at the right time, if I don't do it.''



Radley stirred, reacting to the noise of the groundskeeper's footsteps.  I held his collar to keep him from attacking.



I moved Radley, stood and faced the groundskeeper.  I could see the whites of his eyes in the gloom, even through the glare of the flashlight.  He was older, round-faced, with a potbelly, his hair a bit too long.



His look was wary.  The girl in a black body suit complete with gray body armor, in the company of a small dog, sitting by a grave.



``I'm sorry to intrude,'' I said.  ``I'll leave.''



He peered at me, then glanced at my mom's headstone.  ``You're visiting?''



``My mother.''



``Not causing any trouble?''



I shook my head.



``I won't begrudge you that, so long as you don't cause any trouble or leave any mess.  You clean up after that dog.''



I nodded again, silent.  I didn't have bags, but I had bugs.



His expression softened a touch.  ``You need anything?  I'll be making some tea before I get another walk in later tonight, but I could brew a spot of coffee if you think you'll be sitting out here for a bit.''



I felt tears in the corners of my eyes.  Odd, that they hadn't appeared earlier.



``Tea would be\ldots'' I struggled to find the word.  I almost said \emph{lovely}, but it sounded wrong.  ``Tea, please, if it's no trouble.''



``I'll bring out a cup.''



``And paper?''  I blurted out the words.



``I only have printer paper, I think.''



``That's fine.''



``How many pages?''



I opened my mouth to say, but I had no idea.



Again, a gentle expression that I didn't deserve crossed his face.  ``I'll bring you a good amount.  You bring the leftover back to my office when you return the teacup.''



``Thank you,'' I told him.



It was a little while before he arrived with the tea, the paper and a pen.  I didn't speak to my mother's headstone in the meantime, and even after the groundskeeper stopped by, I couldn't find anything to say.



I wrote; twelve pages, front and back.  It wasn't a fast process.  Two hours passed before the groundskeeper did another patrol of the grounds.  I wasn't sure if it was his job or a thing he did because he had nothing else to do, but he finished up and retired in a little house a little ways up the hill, turning in for the night.



My hand was cramping and I had a stitch in my neck by the time I'd decided I was finished.  Too many hours spent writing with the paper pressed against the armor on my leg, considering how to phrase things, knowing that there was no perfect way to say it.



I penned the final words:



I love you, dad.  I'm sorry
-Taylor



I removed the flower from the vase, and laid it at the foot of the headstone.  I rolled up the paper and slid it into the vase, then placed it upside-down so the rain wouldn't filter inside.  My dad would be the only one to see it.  If someone like the groundskeeper investigated, I didn't particularly mind.



I stood, stretching.  Radley wagged his tail at me, excited to be moving again.  He was a happy, easygoing little guy.  Had Rachel sent him with me with his personality in mind?



I thought about saying something more to my mom, but the illusion had been shattered.  I'd made a decision, and it wasn't one I'd been prepared to make when I'd left the PRT headquarters.  Talking had helped to clarify my thoughts.  I didn't feel as lost as I had, nor as frustrated.  I'd been able to pen out an explanation for my dad.  Not as long or as in-depth as he deserved, perhaps, but an explanation.



``Thanks for hearing me out,'' I said, acutely aware that she wasn't there, that she wasn't listening.  ``I'm going to be busy, so it'll probably be a while before I drop by again.  Sorry.''



I walked away with a lump in my throat, my head held high, and a direction in mind.





