





Regent's base was in the midst of renovations.  The exterior was tame, unassuming, but the interior was becoming something else entirely.  The floor and walls were being covered in stone tile, suits of armor stood on either side of the doorway, and I could see ornate chandeliers at one side of the room, each individual segment separated from the others by extensive bubble wrap.



There was a dais at the far end of the room, almost a stage, with a throne laying on its side on top.  Four people were working in the room.  Workers Tattletale had hired, who would get enough steady employment and money to reward their silence.  Two were working on the walls, one worked on the floor, and the fourth was preparing the dais so the throne could be bolted into place.



``Found it,'' Regent said.  He raised his scepter, tossed it into the air and let it spin twice before catching the handle.



I winced.  ``Careful.  You really don't want to catch the wrong end and electrocute yourself.''



He only chuckled.



``It's daylight.  It's fucked up that we're doing this in the middle of the day,'' Imp groused, as we ventured outside.  Atlas was waiting, and started half-crawling, half-flying alongside us.



``What does it matter to you?'' I asked her.  ``It's not like it makes any difference with your power.''



``It's the \emph{principle} of it,'' Regent said.  He was walking briskly to keep up with Imp, Atlas, and me.  Despite everything we'd been through, he wasn't one to exercise or take care of his body, and he huffed just a little to keep his breath. ``This is the sort of maneuver you pull in the dead of night.''



I shook my head.  ``Circumstances are ideal right \emph{now.  }You don't handicap yourself by trying to conform to any preconceived notions.  Keep a goal in mind, look at everything through the lens of that goal, and look for paths to get what you want.  If they're prepared for you, you strike from an unexpected direction.  If everyone else is expecting a maneuver from an oblique angle, you take a direct route.''



``See, that sounds like a whole lot of work,'' Regent said, ``Constantly thinking about that stuff.  When do you sit back and chill out?''



``Either you make that kind of thinking a part of yourself, you lose a little sleep to achieve that `me' time, or you don't get to relax,'' I said.



``Doesn't sound fun at all,'' Regent said.



``If it was \emph{easy} to take over a city, more people would have managed it,'' I said.  ``This is \emph{work}.  There's always more to be done, whether you're dealing with your enemies, dealing with your subordinates or coordinating with your allies.  If you find you have free time, you're probably fucking up.''



``Or!'' he said, raising a finger, ``I could delegate.''



``That's a recipe for failure,'' I told him.



``My dad managed it.''



\emph{Heartbreaker}, I thought.  I was put in mind of the images of Heartbreaker that had made the web.  The villain, by virtue of his personal, \emph{extensive} harem, had a whole cadre of women virtually climbing over each other for the chance to fawn over him and worship him.  The pictures were a consequence of that, released by his `girls', as Regent had termed them.  Each picture depicted a man in his thirties or forties, depending on the time the picture in question had been taken.  He had black hair, the scruff of a beard, and was invariably seen sitting or reclining on couches and beds, often shirtless, with women at the periphery of the image.  He \emph{oozed }confidence and raw sexuality, languid, more lanky than athletic.



I could envision Regent in a very similar picture.  Years older, grown to his full height and proportions, surrounded not by women, but by the people he had claimed as his \emph{tools}.  Capes he controlled with his power.  Acceptable targets perhaps, people who would be destined for the Birdcage or long sentences in prison, but still \emph{people}.  A different underlying theme than sexuality: Regent would be sitting casually on his throne, pampered in a very different way than I'd seen with his father, having been fed, washed and dressed by a half-dozen pairs of hands working in unison.  Regent controlled people so absolutely that he would essentially be pampering himself; it was a charade.  Almost the inverse of his father, in some ways, but still narcissistic at its core.



The idea bothered me more than I wanted to admit, and it bothered me in a way I couldn't put my finger on.  Did I not want him to become that?  I \emph{did}.  I \emph{wanted }him to be powerful, and that was what he'd naturally become, given his personality and powers.  I \emph{wanted }him to customize his lair like he was, because he'd inevitably have people he was controlling in there, and it would be worth a thousand times the amount it cost if it helped him convey a certain image.



Maybe part of it was the ease with which I could put Imp in that imaginary crowd of people who were waiting on him hand and foot.



I'd have to talk to Grue about that.



``You've gone quiet,'' Regent said.



``Oh!'' Imp closed the distance between us, wrapping both of her arms around one of mine, ``Did he win the argument?  Tell me he won the argument.''



``We're \emph{discussing}, not debating,'' I said.



``People say that sort of thing when they're losing,'' she said.



I ignored her.  ``I was just wondering, Regent\ldots do you \emph{really} want to follow in your dad's footsteps?''



He didn't respond right away.  He looked away from Imp and I both, as if he were idly observing the scenery.



``You're a little bit of an asshole, aren't you?'' Regent asked.



``Only when I have to be,'' I said, mildly surprised at the reaction.



``Fuck it,'' Imp said, letting go of my arm.  ``Us two lesser members of the group need a little victory here and there.  Need to win arguments, get more rep.''



``That's why we're here,'' I said.  ``If everything goes well, today should serve \emph{several} purposes, and one of those was that I wanted to see how you two are operating.''



``Great,'' Regent commented, giving Imp a look.  ``Mom's watching over us, making sure we're doing it right.''



``For any of our enemies with the sense to realize it, you two are the scariest members of the Undersiders,'' I said.  ``Let's focus on \emph{using} that.''



``I'm already using it,'' Imp said.



``Probably,'' I replied.



``You mean this is about \emph{me},'' Regent said.  ``You ask us both to come along to tutor us in how to freak people out, but Imp doesn't need any help, so this \emph{has} to be about me.''



I suppressed a sigh.  \emph{These two}.  ``Not only you.  Imp was doing a terrific job of terrorizing troublemakers in the territory she shared with Grue.  She graduated to owning her own territory, and the fact that she's there has been keeping Valefor and Eligos at bay.  That's good.  But it can't hurt to get an objective opinion and find out how to do it \emph{better}.  \emph{I} do that, with Grue and Tattletale's feedback.''



``I'm versatile,'' Regent said.  ``Give me credit.''



``I'm not saying you aren't, I'm saying we can always stand to improve,'' I replied.



Regent tossed his scepter into the air and caught it.  It bugged me, the idea that he might accidentally taze himself and collapse, with some bystander catching the thing on video.  He \emph{knew} it bugged me, and it was undoubtedly a very deliberate way to get on my case.  I ignored it.



I thought about what Imp had done in Grue's territory; Grue had filled me in on the basics and I'd heard more from people who'd been in that area.  As standalone individuals, none of the members of our team had fully matured.  We were finding our way, figuring out the roles we wanted and needed to take, adjusting our images.



Who would Imp be, a couple of years down the line?  It was maybe bizarre to think about the future, with the way Tattletale had outlined the possible ends of the world, but it was defeatist to let things slide because things \emph{might} end prematurely.  I'd seen Imp change from someone on the periphery of the group, struggling to find a position, to a lesser terror.  She'd cut down superpowered clones with ease, and she was fearless and reckless in a way that could only ease her journey down a bloodier path.



Would Imp become an assassin?  At age eighteen or twenty, would she be an unholy terror, coldly and remorselessly executing enemies who couldn't even be aware enough to guard against her?  If Tattletale erased all records of Imp, if we employed measures to restrict people from tracking her on video cameras and the like, what might Imp become?



Both Regent as a successor to Heartbreaker and Imp as a murderer with a body count were \emph{possible}.  Even \emph{likely.}



I wasn't entirely sure what to do about that.  With Imp, maybe I could have words with Grue, but Regent\ldots



I was still thinking on the subject of Regent, searching for an angle I could use to convince him, when I was distracted.  My swarm noted a number of soft movements, like a flurry of leaves in the wind.



Autumn was months away, there weren't many trees around, and there wasn't wind.



``Found them,'' I said.



``Which?'' Regent asked.



``Haven.  The Fallen will be nearby.  We've got Rosary in a combat mode, and Halo's not in the air, as far as I can see, so they're obviously geared up for a fight.  In your territory,'' I said, eyeing Regent.



``I could've done something if Tattletale called \emph{me} first.''



I drew myself against a building, increasing the number of bugs I was using to scout for trouble.  ``What would you have done?''



``Waited until they were done fighting each other, go after the stragglers.''



``There's a lot of flaws with that idea,'' I said.



He shrugged.  ``I'm flexible.  I could figure something out.''



The more I thought on it, the less sure I was that there was any way it'd really work.  It was an easy way out.



I had a growing suspicion that Regent was interested in being in charge for more for the sake of being in charge than anything else.  It made his position tenuous because he wasn't doing much to hold it.  If this was his modus operandi, then he risked being seen as more of a hyena that preyed on the weak than someone powerful.



``So\ldots if Haven won, they'd arrest Valefor or Eligos, cart the pair off to jail and then leave.  What would you do?''



``Don't know.  Would have to see the situation for myself.''



``Or if Valefor won, what would you even do?  The members of Haven would be too dangerous to get near.''



``Again, I don't know,'' he said.  He glanced at Imp.  ``Today's going to be a fun day.''



I frowned.



Rosary wasn't close, but her presence was unmistakable.  Bugs I'd settled on a car were scattered into the air, carried aloft on paper-thin slices of stainless steel and glass.  I had them take flight, returning in the general direction of the car, measured the progress of her power as more of the debris filled the air, surrounding her.  I knew of her from some internet browsing and a few videos, but this was concrete information.  They were details I could use in the event that I had to fight her.



Three or four seconds in all, for her power to erase the car, scattering it into the air as a storm of incredibly light, thin flakes of matter.  Those same flakes flew around her like a tornado.



She raised one hand, covered in a fingerless glove with hard, metallic feathers or scales at the edges. The storm of petals altered in direction and intensity, the flakes flying forward.  A small few of my bugs died where the flakes struck them at the right angle and speed.  A storm of tiny, fragile blades.  A lot of the petals were actually bouncing off of my wasps, bumblebees and cockroaches, leaving me suspicious that it would take a good while to kill someone with her power.



Up until the point where the petals converged together, reforming into a car tire, ten feet in the air.  A man hurried to leap out of the way before it struck him.  I realized it was Eligos.  He wasn't wearing the Endbringer costume.  Something similar, but without the same theme.  He hurried out of the way as more tires appeared above him.



``We're going on the offensive,'' I said.  ``We don't come out looking like the top dogs if either of the two groups win.''



``We sucker punch them,'' Regent said.



``Better to forewarn them \emph{just} enough that it doesn't feel like a sucker punch,'' I told him.



``Don't you get it?'' Imp said.  She feigned a condescending tone, ``It doesn't count if we don't do it the hardest way possible.''



``It won't be that hard,'' I told them.  I closed my eyes.  ``Let's focus.  Rosary.  Deconstruction and reconstitution of matter, minor telekinesis with the fragments she creates.  Apparently she can take things apart and then reform them so they fall on you.''



``Not a problem,'' Imp said.



``Eligos manipulates wind, creates blades of telekinetically altered air that grow as they travel and boomerang back to him.''



``You'd be better at handling him,'' Regent said.



``His wind will probably mess with my bugs.  We take him together.  One-two punch.''



``Right.''



``Halo packs a special ring.  Kind of like Sundancer, but the thing doesn't burn.  It's a hoop with a cutting edge, and it acts as a forcefield generator and spits out lasers.''



In the distance, Rosary was blocking Eligos' path by reconstituting two trucks, blocking off one road.



``I take Halo?'' Regent asked.



``Do.  That leaves Valefor.  I've got him,'' I said.



I paused, bringing my swarm to the battlefield.



I'd used Atlas to travel to Regent's territory, and I'd walked a short distance.  Throughout, I'd been gathering flying insects and bugs.  I'd been forming silk threads and cords.



Now they rose, flying in formations, just over the tops of the buildings, as they approached Rosary and Eligos.  They meshed together into a barrier, nestled close enough to one another to filter out sunlight.



The area darkened visibly, and the droning of the bugs filled the air.



Rays of golden light speared into the swarm.  They were persistent, unending, five steady beams that concentrated on areas where the bugs were thickest.  Halo.



That left only one unknown.  Valefor had to be somewhere nearby.  The second he got a glimpse of me, it was over.



My swarm hit Eligos and Rosary.  Eligos created a strong wind that whipped around him, driving the bugs away.  Rosary used her power to shred the silk lines.  In the face of the biting insects, however, she couldn't do as much.  The petals around her cut into the swarm, but it was minimal damage to a great many attackers.



She gathered the petals together to create a car without either wheels or a driver's side door, and though she'd formed it with some bugs trapped inside, she climbed in and had the petals reconstitute into a door, creating a perfect seal.



Eligos put an end to that when he sent a blade of wind at the back of the car, shearing one corner of the vehicle.  My bugs flowed into the open area, covering Rosary from head to toe.  Her mask was hard, around her eyes, cheekbones and nose, ending in a sharp point, an etched metal plate, worked into her hood.  It didn't cover her lower face and it surrounded but didn't cover her eyes.



``Come, and stay close,'' I said, drawing the bugs around us.  I walked briskly forward.  Rosary had her petals, I had my bugs.  If Valefor wanted us, he'd have to be clever.  ``And Regent?''



``What?''



``I'm going to ask you a question later, and I'll have my arms folded.  I want you to lie.''



``Lie?'' Imp asked, aghast.  ``So dishonest!''



``We're \emph{honest} villains, Skitter,'' Regent said, taking a stern tone.  ``We \emph{ear}\emph{n} our victories the right way, not through deceit and dishonesty.''



I rolled my eyes.



As we approached, I found Halo in my reach.  My swarm approached him, and his halo zipped to his side, five feet in diameter and razor-edged.  A force field protected the hero.



He was still rooted in place.  One less person to deal with.



``Regent,'' I said, touching his shoulder.  My bugs spread out to create a clearing around us, and I pointed.



He turned to face Eligos, and I parted the bugs. Eligos was wearing only the bodysuit that went under whatever armor he'd been wearing, and a mask that covered his face, leaving only one eye exposed.



With a wave of his hand, Regent knocked Eligos over, causing one leg to buckle just as the other was involuntarily straightened.  Eligos sprawled, and the wind briefly cut out.  My swarm descended on him, and I began binding him in silk.



I had Atlas take to the air, as I worked more silk cords into the surroundings.  ``Be nice if this works.''



``What are you doing?''  Imp.  Her presence caught me off guard.



``Threads,'' I said.



``He can cut threads,'' Imp commented.  ``It won't work.''



``I know he cuts threads,'' I said.  ``Watch.''



Atlas passed over a space between two buildings, then dropped out of the sky.  The string that extended between him and Eligos went taut.  I had a series of threads strung between two buildings, and Atlas served as a counterweight, so Eligos could be hauled into the air.



``No way that holds,'' Imp said.



``Never intended it to,'' I told her.



Mandibles severed the thread, and Eligos fell.  Three stories, give or take, and he landed on all fours.  He screamed, and wind ripped through the area, scattering both bugs and petals.  Eligos flopped over onto one side.



``Two left.  Rosary and Valefor,'' I said.



Rosary had disintegrated what remained of the car and was facing me, the multicolored petals a tight storm around her.  I could only make out glimpses of her general silhouette.  The rest I could fill in from my research.  A young woman in a rose-tinted robe with gold leaves at the edges, and a gold-colored mask.  She was silent.



``We have no quarrel with you,'' she said.  ``We're only here to deal with the Fallen.''



``Then kneel,'' I said.  I banished the bugs, and she almost staggered in relief, after holding firm against their onslaught.



She straightened her back and squared her shoulders, but didn't respond.



``Kneel.  This is our territory.  If you pay the proper respect, I hand you Eligos and Valefor, and you can leave the city with no problems.''



``I could drop a car on your head.''



``And I could take you down as easily as I did Eligos.''



``Without silk?''



``Without silk,'' I said.



She nodded slowly, then slowly knelt, dropping to one knee.  Her eyes, behind her mask, were glaring at me.



``What would you have done if I hadn't?'' she asked.



``Not my style to give away plans to the enemy,'' I said.



``You could be bluffing.''



``I'm not.  I would have disabled you, knocked you out and Regent would have used his power to seize control of you.''



Her eyes widened a fraction.



``Regent, you can use your power on unconscious people, right?'' I asked.



Regent shrugged, ``Obviously.''



There was the lie.



``That simple,'' I told Rosary.  ``He can assume control instantly, once he's had control over someone once.''



``That crosses a line.''



``I'm \emph{far} less concerned about crossing lines these days,'' I told her.  ``But you only broke one rule.  We'd let you go, with the idea that we'd seize control of you if you ever came back.  We'll do that with anyone and every--''



I stopped.  Imp had appeared at a grocery store nearby.  She was speaking in a low voice, murmuring.



``\ldots{}Skitter said she'd take you on and she can use her bugs to attack you without being seen and she can hear and see this so she knows\ldots''



``Fuck!'' I growled the word.



``Valefor got her,'' Regent drew the obvious conclusion..



``I told her to stay close,'' I said, breaking into a run.  Rosary wasn't even a consideration.



``She's not the type to listen!''  Regent huffed.  Rosary started to follow us, then hesitated, glancing at Eligos.



``\emph{Watch him}!'' I barked the order, augmenting my voice with the combined drones, chirps and buzzes of all the bugs in the area.  The heroine stopped where she was.



Regent and I were thoroughly shrouded by bugs when we reached the grocery store.  There were only a handful of people inside, every one of them rooted in place.



Stranger-type capes were classified that way due to their capabilities in stealth and subterfuge.  Valefor was more the latter.  He wasn't \emph{stealthy}, exactly, but his ability to perpetrate subterfuge was devastating.



One look, and his target was stunned, rendered eminently suggestible.  A hypnotic gaze, so to speak.



He'd played up the telepathy angle before people caught on, and the costume that echoed the Simurgh was a token to that.  The fact that he could leave suggestions that only triggered under certain conditions was another part of it.  `Attack so-and-so next week'.  `Set fire to your workplace the next time your boss pisses you off'.



Capes with powers that allowed them to compel others walked a fine line.  Even without murder, Valefor was pushing that line.



``To everyone listening, if that swarm or any of the people inside move away from that spot, or if something happens to me,'' a young girl spoke in a man's voice, stepping out of the sheltering embrace of a middle-aged woman. ``Kill yourselves or do your best to kill \emph{them, }I don't care which.''



I'd taken her for a scared kid in the company of her mother.  No.  She'd\ldots \emph{he'd} compelled a woman to pretend to be his mother, and my roving insects hadn't thought twice about it.



It was Valefor, in a teenage girl's top and skinny jeans, with long, straight blond hair, and makeup caked onto his face to hide the tattoo.



``\ldots{}and forget I gave these orders,'' he finished.



That would be one reason for the stranger classification, right there.



The orders to kill or commit suicide were a surprise to me, but he was more than capable of covering his tracks.



``Imp,'' Valefor said.  ``Find and kill your teammates.  I want you to kill yourself when you're done trying.  Go, and forget I gave this order.''



Imp drew her knife with one hand and her taser with the other.  She paused a second, and then charged for Regent and I.



I tensed.  I had options, but if any of his hostages read it as a cue to kill themselves-  no.



I could shoot from the midst of the cloud, but then we'd be paralyzed.  There was no guarantee that Valefor's influence would end with his death.



I'd told myself I'd be heartless, but this wasn't what I'd meant.



Imp turned a right angle, moments before plunging into the swarm.  She charged for Valefor.



He reacted, giving an order, ``Everyone listening, kill yo--''



He didn't get any further.  She kicked, directing the attack between Valefor's legs.



Valefor hit the ground, and Imp kicked him between the legs once more for good measure.



``Cancel the orders, fuckwit!'' she growled, dropping on top of him.  Her knife pressed against Valefor's throat.



``How--''



She backhanded him across the face, striking him in one cheekbone with the knife handle.  ``Cancel!''



I could sense the crowd relaxing.  People hurried away from the scene.  It took more than a minute before they were all gone.



Imp struck Valefor again.



``Stop,'' I said.



``Regent got one in, I wanted one too,'' she said.  She spat at Valefor.



I tentatively moved bugs, then settled them around his eyes.  Valefor struggled, but froze when Imp pressed the knife against his throat.



\emph{Regent got one in?}



Oh.



``You\ldots \emph{voluntarily} gave him control over you?'' I asked.



``Little while back,'' Imp said.  ``I wanted to see what it was like.  Could come in handy.  \emph{Did} come in handy.''



\emph{It's Regent}, I thought.  I'd fought beside him in life and death scenarios and I would never have allowed him to take control of me.  Couldn't fathom it.



Was there a way I could diplomatically say as much?



None I could think of, right this minute.



``I can't imagine submitting myself to that,'' I said.



``Riskier for you,'' she said.  ``For me, his power over me shorts out when I use \emph{my} power, and that's any time he slips up or goes to sleep.  Then he forgets who I am, and I'm free to come after him and fuck him up.''



``Eviscerate me in my sleep,'' Regent said, too jovially.



``Exactly,'' Imp said, sounding just as pleased with herself.  ``And I know him.  He's not about to fuck with me with the amount of work it'd take to keep track of me.''



``Told you, Dork,'' Regent commented.  ``I'm versatile.''



I didn't have a response to that.  I glanced at Imp.  ``Tell me something only Imp would know.''



``\emph{Seriously}?'' Regent asked.



``I could tell you that there's a mole on your back,'' Imp said.



That took me a second to process.  When had I ever had my clothes off where she could see?



Not her.  Brian.



``You were \emph{there?}''



``I stopped in.  I wanted to see if my brother was okay.  Believe me, I wish I hadn't.''



\emph{She was there}.  \emph{Then}.



``Wait, what's this?'' Regent asked.



``It's not important,'' I said, my voice tight.



``I'll tell you later,'' Imp said.



``Don't,'' I said, in a warning tone.



There was a pause.  I could tell the pair of them were having too much fun at my expense.



But there was still an enemy to deal with.



She looked down at Valefor.  Her tone was more serious as she said, ``I didn't think this man-slut would be able to see me.''



``You know his powers,'' I said, glad for the change of topic.  ``Hypnotic stare, Tattletale said he might have other senses or augmented awareness to track his victims.''



``It's fine,'' Imp said.  She adjusted her hold on the knife.  ``Worked out.''



``Yeah,'' Regent said.



``I guess you two got a victory,'' I said, ``A little\ldots what did you call it?''



``Rep,'' Imp said.



``Rep.''



Long seconds passed.



``I could control him,'' Regent said.



``What's the point?'' Imp asked.



``It'd be an advantage,'' I said.  ``And I suppose it's up to you two what we do next.  It's your territory, Regent.''



\emph{And I want to see how you operate, when left to your own devices}.



``Pain in the ass,'' Regent said.



``We let him go, he's going to come after us,'' Imp said.



``Probably,'' I agreed.



``You want us to turn him in,'' Regent told me.



``I'm not saying that,'' I answered.



Regent studied me, ``You're here for a reason, and it's not just babysitting us, being an overbearing boss and making sure we do the job right.  Let's not waste time.  Out with it.''



I kept my voice low, so Valefor couldn't hear.  ``I said you and Imp were the scariest members of our group.  You heard what I said to Rosary.  How I was going to let her believe that we could take control of her at any second, so long as she's in the city.''



``Sure.''



``Fear.  Ruling through fear.  How do we get the maximum result for the minimum effort?''



``I like the sound of this,'' Regent said.



``We make our enemies paranoid,'' I told him.  ``We get them scared enough that they start devoting more effort than is necessary to dealing with us.  Feed them misinformation.  With your power, we have an easy way to keep any enemy we capture from wanting to enter the city, and so long as we let them go, rather than \emph{using} them, we're not drawing enough heat to get a kill order put on our heads.''



It was the best I could do.  This was the crossroads, as far as I was concerned.  If he didn't take to this idea, the Regent I'd envisioned was likely to come to pass.  If he \emph{did }accept the idea\ldots well, it was still likely, but I could have hope.



``Huh,'' Regent said.



Apparently that was the only answer I was about to get.



``What do we do with him?'' Imp said.  She had the knife in Valefor's mouth.  ``I'm going to get a cramp, leaning over him like this.''



``We can hold onto him long enough for Regent to seize him,'' I said, ``Then let him go.  Or turn him into custody.  But there's no guarantee he wouldn't use his power to control someone and turn them into an unwitting assassin.''



``If he hasn't already set some up,'' Imp said.



``If he hasn't,'' I agreed.



I thought briefly of my dad.  If Valefor had been feeling malicious\ldots



I put the idea out of my head.



``We could trust the PRT to look after him,'' Regent said, somber.  ``They're professionals, they know how to deal with dangerous villains.''



He didn't manage to hold it in for long.  He chuckled in near-silence, his shoulders shaking.



``The other possibility,'' I said, ``Is stripping him of his powers.''



I reached behind me, and found a small metal container.  I tipped out the contents into my palm, and then held out my hand so Regent could see.



``Seriously?'' Regent asked.



``Seriously.''



``If you're up for it\ldots'' Regent trailed off.



``I'm done with holding back,'' I said.  ``Decisive action.  No mercy for those who don't deserve mercy.''



``Right,'' Regent said.



I approached Valefor and Imp.



Valefor heard the footsteps, must have felt the impact as I stepped forward, standing over him.  He shook his head violently, oblivious to the knife Imp had placed in his mouth.   That, or he'd overheard something I'd said and didn't care anymore.



He managed to shake enough bugs off that he could open his eyes.  He fixed his gaze on me, and I froze.  My thoughts dissolved to warm, wet, white noise.



The maggots, millipedes and centipedes dropped from my hand.  A part of me that was aware without being quite \emph{conscious} controlled them, carried out my intent.  They spilled onto his face, and moved toward his eyes.  The stronger bugs helped pave the way for the others, leveraging the eyelids away from the eyes so the maggots could pass beneath.



``No!'' he shouted, around the knife.  ``Sto--''



Imp shifted position.  She was kneeling on his chest, and she moved the knife, bringing one knee into Valefor's chin.  I could feel the force of the impact through the bugs on his face.



``Oh god,'' Imp said, ``Gross.  Gross, gross, gross.  Did I get any of them on me?''



My thoughts were clearing.  I blinked, and the movement felt painfully slow, as though I were almost asleep.



``You didn't get any bugs on you,'' I said, stepping on Valefor's right hand.  Imp held his left with one hand, and held the knife's blade against Valefor's makeup-caked lips.  He groaned and writhed beneath her grip.



``They \emph{stink},'' Imp complained.



``You're imagining it.''



``I'm really not.''



Valefor's struggles continued.  His writhing intensified, and it got to the point where he had to turn his head to throw up.



When he turned his head my way, his eyes moved over me, unseeing.  His chest was heaving as though he'd just run a long distance.



``Let him up,'' I said.



Imp backed off, We pulled Valefor to a standing position.



``Walk,'' I told him.



He was almost \emph{defeated} in demeanor as we marched him in the general direction of Rosary.  He looked like he had tears streaming down his face, but it was only the leaking vitreous fluids.



``Fear,'' I said.  ``Remember what Bakuda said?  You have to be unpredictable, but you balance it with \emph{certainties}.  Realities.''



``It's a little fucked that you're taking cues from the psycho bomb girl,'' Regent commented.



``Yeah,'' I said.  I wasn't about to deny it.  ``But I'd prefer more certainties than unpredictable elements.  The punishment fits the misdeed.''



\emph{And if you take that to heart, then today's worth whatever bad karma I reap from this}, I thought.



``The look on Rosary's face is going to be \emph{delicious},'' Imp said.  ``Doesn't Haven have a major hate-on for the Fallen?''



``They do,'' I said, ``But when we meet her, don't say anything.''



``What's the fun in that?''



``It's the \emph{effect},'' I said.  ``Trust me.''



``What's in it for me?''



``I'm supposed to bribe you?''



``Fo' sho,'' she said.



``Ice cream,'' I said.  \emph{I can't buy ice cream as Taylor anymore}.  ``I'll pay for it, you pick it up.''



``Sweet!''



Rosary was on guard as we approached, her stance intensifying as she recognized Valefor.  The petals were a storm around her.



I shoved Valefor, and he tripped and sprawled in front of the heroine.



She stared down at him.  He raised his head, and I could see her tense.



``I was expecting medusa's head,'' Rosary said, when Valefor hung his head again.  It looked like he was trying to avoid gagging.



\emph{What?}  I could remember the myth, but\ldots what?  I kept my mouth shut rather than ask.



``He's blind,'' she voiced the realization out loud.  ``You blinded him.''



I nodded, still silent.



``Permanently?''



I had to give a response, now.  ``He'll need antibiotics.  Both Valefor and Eligos will need medical care.  It's up to you whether you save his vision.''



``Just like that.''



I nodded once.



``We had it handled,'' she said.



``Our city, our business,'' I said.  ``Next time, \emph{ask}.  We'll deal with it.  You leave, now, and you ask permission before you set foot in Brockton Bay again.''



``Or we can expect a fight.''



``Expect consequences,'' I said.  I looked down at Valefor.  ``See to his eyes.''



I turned and led the other two in walking away.



``What--'' Regent started.  I held up a finger.



When we were out of earshot of Rosary, I dropped the finger.



``What's with that?'' he asked.



``We got what we needed.''



``You didn't even mention how you blinded him,'' Imp said.



``It's about using fear as a tool,'' I told her.  ``The unknown is always better than the known.  Silence is better than almost anything we could say.  For example, you can leave them wondering just why Valefor's power didn't work on you.  And consider the reaction when they realize just \emph{why} he's blind.  Maggots packed into his eyeballs.''



Imp shuddered visibly.  ``How?''



``That's the exact question they'll be asking,'' I told her.  ``In case you're wondering--''



``I'm not.''



``--Centipedes and bigger bugs opened a path through the external layers.  Maggots crawled inside.  Nothing critical damaged.  Probably repairable, though I'm not an expert in anatomy.''



She shivered again, ``My eyes are watering.  Total heebie-jeebies.''



I didn't reply to that.  I was more focused on Regent.



``We okay?'' I asked him.



He shrugged.  ``Sure.''



Noncommittal response, no clue as to whether he'd take my suggestion on using his power to scare people away without creating a harem like his dad.  I hadn't really expected anything else.



``So gross,'' Imp muttered.



But he had the ability to take control of Imp.



I needed to have a discussion with Grue.  A very careful discussion.





