





Had Tagg done me a favor, by getting me to think along these lines?  For what felt like too long, I'd been overly focused on the \emph{now}.  Getting through the next few days, surviving, staying sane, parceling out the time I had to relax and striving to find moments where I could feel safe.  That state of mind hadn't started when I put on my costume.



Odd, to be taking someone's words to heart, when I had so very little respect for them.



I was in plainclothes, and they were clothes I wouldn't normally have worn, which was sort of the point.  The idea was to be hidden in plain sight, as I walked in the midst of the crowds downtown.  I'd removed my glasses and regretfully donned contact lenses, slathered on sunscreen and donned a white summer dress and sandals, along with a big, wide-brimmed sun hat that was incongruous enough to mark me as a possible tourist.  Shopping bags and loosely braided hair helped complete the image.



Maybe the sun hat was conspicuous.  The clouds were heavy overhead, and the wind was moving them across the sky at a decent pace.  Hopefully it would brighten up.



If anything would give me away, I suspected it'd be my eyes.  I eyed everyone that crossed paths with me, looking at them without looking \emph{directly} at them, watching for that glance and that restrained reaction that might suggest I'd been spotted.



Were that to happen, I'd change direction, take a different route to my destination.  If that wasn't enough to shake the attention, well\ldots I did have my bugs, flowing through my hair, beneath my hat and between the dress and my bare skin.  I had weapons, my costume and more bugs in the shopping bags, beneath the shoeboxes and spare clothes I'd put over top of them.



I stopped at an intersection, and was briefly relieved of the need to watch the people around me, free to look at their movements as a whole.  The crowd was moving like a river, separating into streams of people who moved through the streets that had open shops and restaurants, avoiding the ones where construction was prevalent.



I detoured into one of those construction-heavy side streets, fully aware that I was abandoning the `hide in plain sight' ploy.  It didn't matter.  Nobody could really see my face, and I had my bugs.



There were a few crude catcalls from the construction workers at the sites to either side of me.  Not because I was attractive in any way, I suspected, but because I was over fourteen, under forty, I weighed less than two hundred pounds and I was wearing a skirt.



This area was the site of the fight against Echidna.  Walls bore the marks of laser blasts and gunfire, blood still marked the streets here and there, and there were divots and holes in the road, surrounded by rings of bright spray paint so pedestrians wouldn't step into one and break an ankle.  Holes created by blasts of energy, small explosions, large explosions and the heavy footfalls of a gargantuan monster with clawed toes.



Bugs notified me about a change in the wind before the wind even reached me.  I already had my hand on my hat to keep it in place as hat, hair and skirt were stirred by the gust.  The weight of the swarm bugs that clung to the inside of the dress helped to keep it in place.



I found I was tense, as the wind dissipated, the muscles of my legs tight, ready to shift me to either side, to push me into the air with a leap or throw me to the ground.



But it was only a strong breeze.  Rosary was gone, I hoped, or she'd be gone soon.  We'd taken care of Eligos and Valefor yesterday.



It would be so easy to get paranoid over the slightest things, if I let myself.  Parahumans kind of opened a lot of doors on that front.  There was no way to be on guard against every eventuality.  Bystanders could have been manipulated by Valefor before we confronted him, cloth in store displays could be Parian's work, the mannequins some trap laid by, well, Mannequin.  The ground, the wind, changes in temperature, shadows\ldots anything could be a sign of incoming attack.



Not that I was in a position to complain, but\ldots was it any surprise that capes tended to get a little unhinged as they grew in prominence?



I reached one construction site with plywood strapped to a chickenwire fence, protecting the interior, grafitti painting the plywood with a large face.



\emph{Eye on the door}, I thought.  I let myself in.



Grue and Citrine were inside, both in costume.  Citrine in her yellow evening gown and mask, adorned with her namesake gemstones for both jewelry and embellishments, a file folder tucked under one arm.  Grue, for his part, was wreathed in darkness.  They couldn't have been more different in appearance: sunshine and darkness.



But both, I knew, were professionals.  I suspected they were very similar people.



A part of me felt like I should be jealous that the pair were keeping each other company.  Except, rationally, I knew they weren't.  Rationally, I knew there was no reason they'd be together, or even that they'd be attracted to one another.  Citrine was pretty, but\ldots I couldn't imagine she was Grue's type.



Why did it bother me that I wasn't jealous, then?



``Skitter?'' Citrine asked.  She looked me over.



``Yes,'' Grue said.  ``Hi, Taylor.  You look nice.''



``Thank you,'' I said, and despite my efforts, I smiled.  I'd sort of hoped to maintain the contrast between appearance and demeanor.  No major loss.  I looked at Citrine, ``You wanted to meet?''



``I have a few points to go over, details my employer wanted to raise.''



``Nothing troublesome?''



``It depends on your response.  I don't think it's anything troublesome.  Keeping you abreast of his operations.''



``No complaint here,'' Grue said.



``I expected Tattletale would be here.''



``If it's alright,'' Grue said, ``We'll record the conversation and pass it along to her.  She's occupied with some other matters.''



``The difficulties of being a thinker,'' Citrine mused.



\emph{More than you know}, I thought.  Tattletale was occupied with little more than an intense migraine.  She'd pushed herself too far and was now paying for it.



I cleared my throat.  ``Any objection to stepping upstairs?  It's too nice a day to stay inside.''



She shook her head.



We ascended two staircases to the roof.  It was sunny, and the wind was strong enough that even the long, dense braid of hair at my back was stirred.  I put the shopping bags down at my feet.



The location had seemed incongruous, even inconvenient, given where Grue and I were headquartered.  I knew that Accord and his Ambassadors weren't anywhere near here either.  Now that I saw our view, I had a sense of why Citrine had asked that we meet here, and the topic of the conversation.



Ahead of us, just a block away, the portal.  A white tower in progress, surrounded by three cranes.  A white tent was framed with a rigging of criss-crossing metal poles, and that rigging was being covered in turn by a solid white building, windowless.  We couldn't make out the base of the building from our vantage point, but I could make out the ramps that led to the interior, like the on-ramps to a highway or the entrance to an aboveground parking garage.  They curved up around the building, a geometrical arrangement like the petals of a flower, and led into the tent at different heights.  There were signs of construction and recent demolition in neighboring lots.  The adjoining buildings would support the main structure: administration and defense.



It was so \emph{complete}, considering that so much about the future of the portal was in question.  Nothing had been confirmed yet, as far as the ownership of the portal.  Accord's design, Tattletale's construction, the government's rules on quarantine.  The government had sent people inside, and Tattletale had followed suit.  It was technically her property, they had no evidence it was anything but the curiosity of an invested businessperson, and they hadn't complained.



Yet.



It was a mingled blessing and curse.  The portal, the \emph{door}, as some were calling it, was taking some of the spotlight from us Undersiders.  There was a great deal of national debate over whether the landowner or the government should get the rights to the property.  I almost wished people \emph{could} ignore it.  Things threatened to get out of control if and when it was verified that this thing was usable.



``Accord is recruiting five new capes to his team,'' Citrine said, interrupting my thoughts.



That gave me pause.  Not the topic I'd expected her to raise.  I turned on the tape recorder, held it up so she could see.  She nodded.



I repeated her statement for the tape, ``Accord is recruiting five new capes.  Who?''



``We don't know yet.''



``You'll let us know who they are as soon as you find out?  Give us a sense of their personalities?''



Citrine lifted the file folder, opened it and handed me a set of pages, neatly stapled.



The entire thing was high-resolution, complete with a picture and lines of text in labeled boxes.  Much of it was neatly censored with black bars.  A young man, in his mid twenties, his hair immaculate, parted to one side, wearing a high quality business suit.  `Kurt', last name censored.  Date of birth censored.  Age twenty-five.



The next page was more details.  Personality tests, psychiatric tests, GPA in middle school and high school, post-secondary education, work history.  `Kurt' had ascended to the role of head chef at a record pace, returned to school to get a four year education in three years, then started working for Accord.



`Pam'.  Contract lawyer for a major firm, made partner at age twenty-eight, stepped down to work for Accord.



`Shaw', `Laird', and `Kyesha' followed the same pattern.



``They are going through the vetting process as we speak.  Experienced members of Accord's businesses, on board with his plans, and loyal,'' Citrine said.



``I'm not sure I follow,'' I said.  I handed the papers to Grue for him to look over.



``My apologies for being unclear,'' Citrine said.



I waited a second for her to elaborate or clarify, but she decided not to.  She wanted us to draw our own conclusions?



``You don't know who they are, but they work for you?'' I asked.



``She means she doesn't know who they're going to be when they get powers,'' Grue said.  ``Don't you?''



Citrine nodded once, the rest of the file folder held behind her back.



``Cauldron,'' I said.  ``Accord's using Cauldron to empower his employees.''



``Yes.''



``Why are you telling us this?'' Grue asked.



``This is your territory and we are your guests.  It's only natural to request permission to bring five new parahumans into the area.''



``Are you a Cauldron cape, Citrine?'' I asked.



``Yes.''



``So you know something about how they operate, then.''



She shook her head.  ``Very little.  We get our powers with Accord serving as the middleman, and I'm not entirely sure how much he knows.  Either I would have to ask him for details, and I have no reason to, or you would have to ask.''



I frowned a little.



``Accord wanted me to inform you that the product has a slight chance of causing physical defects and mental instability.  A possibility of an incident.''



I thought of Echidna.  \emph{No shit}.  More diplomatically, I said, ``And you wanted to warn us, so we were forewarned and forearmed about possible issues.''



``We hope and expect to keep things wholly internal.  There are very few powers I cannot counter, and I will be there to act if something goes awry in any way.''



In \emph{any} way?  Did that extend to physical deformities?  I couldn't see Accord tolerating something like that.  I could have stipulated something, warned them to let the deformed ones go\ldots except it would destabilize the alliance.



``They've been informed of the risks?'' I asked.  ``These\ldots soon-to-be capes?''



``Fully.''



``Why?'' I asked.  ``Why leave a successful, ordinary, \emph{happy} life behind, and go to that risk?  Why work for Accord, of all people?''



``Power,'' Citrine said.  She turned her back to the portal to meet my eyes, her dress flaring slightly with the rotation of her body.



``Power isn't magical,'' I said.  ``It creates as many problems as it solves.''



``Power is less a thing unto itself than it is a journey.''



``To \emph{where}?''



Her eyes were penetrating as she gazed at me.  ``Not all journeys have destinations.  Power is the ability to effect \emph{change}, and people who create change ride that tide, with far-reaching effects.  For some of us, that's something we're born into.  Our fathers or mothers instill us with a \emph{hunger} for it from a very early point in time.  We're raised on it, always striving to be the top, in academics, in sports, in our careers.  Then we either run into a dead-end, or we face diminishing returns.''



``Less and less results for the same amount of effort,'' Grue said.



``Others of us are born with nothing.  It is hard to get something when you don't have anything.  You can't make money until you \emph{have} money.  The same applies to contacts, to success, to \emph{status}.  It's a chasm, and where you start is often very close to where you finish.  The vast majority never even move from where they began.  Of the few that do make it, many are so exhausted by the time they meet some success that they stop there.  And others, a very small few, they make that drive for success, that need to \emph{climb} becomes a part of themselves.  They keep climbing, and when someone like Accord recognizes them and offers them another road to climb, they accept without reservation.''



``Which are you?'' Grue asked.  ``Did you start with power, or did you fight for it?''



Citrine smiled a little, looking over her shoulder at the tower.  ``I suspect Tattletale will tell you, if you're curious enough to ask.''



``And your power?'' I asked.



She arched one of her carefully shaped eyebrows.  ``Tattletale didn't share?''



``Tattletale had some ideas, but nothing definitive.''



``I wouldn't normally share, but Accord told me I should disclose any information you request.  I attune areas to particular functions.''



``To what ends?'' Grue asked.



``More gravity, less gravity, more intense temperature variation, less intense temperature variation.  Friction, light intensity, the progression of time\ldots More possibilities than I can count, many so minor you wouldn't notice.  But if someone \emph{powered} is in the area, and I find the right attunement, as though I were searching a radio station, I can cut off their powers.  If I'm \emph{exact }enough, which never takes more than twenty or thirty seconds to narrow down, I can use my power to cancel out the filters that keep someone's powers in their control.  I can also remove the filters that keep their power from affecting them.''



``Turning their power against them,'' I said.



``Yes,'' Citrine said.



I could picture my bugs slipping from my control, gravitating towards me in response to my stress, biting and stinging, even \emph{devouring} me, perpetuating the stress, pushing the cycle forward.



Or Grue\ldots what would happen to him?  Rendered blind and deaf by his own power, dampening his own abilities until they sputtered out, or creating a feedback loop by draining his own abilities, until he was overwhelmed?



``And Othello?'' I asked.



``He has a mirror self,'' she said.  ``Who walks in a world very similar to this one.  This self has a limited ability to affect our world, and can't be affected by us.  Othello can push himself into that other world to bring his other self into ours, and vice versa.  One leaves, the other enters.  It looks very much like teleportation or invisibility.  It isn't.''



``Accord buys good powers then,'' I said.



``The best.  There would be no point if he didn't.''



``And there'll be five more?  Of your caliber?''



``Allowing for variations in results, yes.''



``What else do you know about Cauldron?''



``Very little.''



\emph{And Accord is sitting out this meeting because he thought Tattletale might be here, and he didn't want her to dig anything up.}



Which meant Accord would be avoiding us, avoiding \emph{Tattletale} from here on out.  That made life easier.  It meant he wouldn't be pestering us or trying to subvert us.  Not to our faces, anyways.



``Five new members is fine,'' I said.  ``Each of them should meet Tattletale on an individual basis.  She'll vet them in ways Accord can't.''



``Agreed,'' Citrine said.



``The deal we struck with Accord stands.  He buys no territory, holds only what Tattletale gives him, and he doesn't get to expand his territory to account for new members.''



``Agreed.''



``How long until they have powers?'' I asked.



``Two days.  We'll devote a week after that to training their abilities and ensuring they meet standards.  Accord likes to hand-craft masks for us, picking out appropriate colors and names.''



``Would he object to giving them the Teeth as a job?  It can be a collaborative effort between Ambassador and Undersider.''



``I'll raise the idea with him.  I have little doubt he'll agree.''



``Good,'' I said.  I turned my attention to the tower.



Citrine looked as well.  ``The door.''



``You've heard the world ends in two years,'' I said.



``Yes,'' she said.



``When Tattletale set up the portal, she made an escape route.  Not for \emph{us}, but for the world.  As much as they're able, they're leaving room for mass-evacuation.  You can't see it from here, but the bottom of the tower doesn't have a road or a ramp leading into it.  If the city cooperates, they can route train tracks through there.  The trains wouldn't even have to slow down as they passed through, if there was enough set up on the other side.''



``Many would live here for the possibility of easy escape alone,'' Citrine said.



``There's also the work,'' Grue said.  ``Making the space on the other side livable, research on the other world, investigating differences in plant and animal species.''



``When I had a discussion with Director Tagg,'' I said, ``He told me to consider where things would stand in a few years.  The doorway is going to be a big part of it.  I'd like to ensure that we still have a presence here, that there's a measure of peace, both from heroes and villains, and that the portal remains an escape route.''



``Any particular thoughts on how things should be arranged?'' Grue asked.



``Some, as far as our group is concerned.  But I'd have to talk to the others about it before I put any ideas out there.''



``Do the Ambassadors fit into that image of the future?'' Citrine asked.



``It depends on Accord,'' I said.  ``You know him better than I do.  Is he stable?''



``No.  Not in the sense you mean.''



My heart sank.



``But you can trust him.''



``I suppose we'll have to,'' I said, not feeling much better.  ``Do me a favor, sound him out on what limits he'd set in terms of bringing others on board.  Other teams, other groups.  Individuals.  We should set standards, hard rules for people in the city and people in our alliance.  I'm not going to mince words.  His response to this is a big factor in how all this plays out.''



``Including his presence in this hypothetical future you're envisioning,'' Citrine said.



I shrugged.  ``You say we can trust him.  I'd like to believe you, and I will, until I have a reason not to.''



``That's all we can ask for,'' Citrine said.



``Is that it?  You wanted to meet to address the recruitment of your five members?''



``No.  Here.''



She handed me the folder, and my arm sagged with the weight of it.  I approached Grue and stood next to him as I paged through it.



It was a three-hundred page treatise, complete with binding at the spine and a gray cover printed with the simple words `Brockton Bay: Crime and Public Safety'.  I handed Grue the folder and the dossiers on the five recruits to the Ambassadors, keeping the tome.  I paged through it, holding it so Grue could read alongside me.



It was less an essay than a technical manual.  A step-by-step guide to bringing the city in order.  Size eight font, bolded and centered headings, annotations, continually referring to other sections.  It was readable, though, almost seductive in how it made it all sound so possible.  The language was simple, clear, and unambiguous, as though it were outlining little more than how to build a bookshelf, without more than the occasional diagram.  There were branching paths, too, clearly outlined, detailing the routes to be taken if something didn't work out.  I could only assume that the bulk of the text was Accord's accounting of all the various possibilities.



No murder, nothing totalitarian.  Not at a glance.  It was merely a \emph{very} involved analysis on Brockton Bay, the various criminal elements, the various players and how things could be brought into alignment.



``I'll read it,'' I said, ``And I'll make sure Tattletale gives it a thorough looking-over.''



``Okay,'' Citrine said.  ``Don't worry about giving him a response.  He already knows.  Nobody ever accepts the proposals.''



``We'll give it a serious look,'' I stressed.  ``Who knows?  Tattletale might get a kick out of being able to debate the finer points of the plan with Accord.''



Citrine arched an eyebrow.



``I'll tell her to play nice,'' I said.



``Then I suppose those are the key points covered.  Thank you,'' Citrine said.  ``If there's nothing else?''



``Nothing springs to mind,'' I told her.



She offered me a curt nod, then headed for the stairwell.  Grue and I stayed put.



The pair of us stood on the rooftop, just out of sight of anyone on the ground.  The portal-tower loomed a short distance away, taller than the surrounding buildings, rippling slightly as the wind pulled at the upper areas where there were only the tent and metal framework.



``So much talk of the future,'' Grue said, ``And no guarantee there'll be one.''



``There will,'' I said.  ``With everything else Dinah said, we know there'll be some kind of future.  It might not be a \emph{pretty} one, but people will survive.  We'll slip away to other dimensions, the best of us will persist, and we'll slowly make our way back to where we are now, but we'll survive.  Or maybe, with all the powers out there, we'll find a way around this, and it doesn't come to pass.''



``And we establish some kind of stability in Brockton Bay?  Bring Accord's plan to fruition?''



I didn't have an answer to that.  I looked down at the book.



``You're skeptical?''



``Skeptical,'' I said.  ``Ever notice how every power gets turned to violent ends?  Even the people with powers that could benefit humanity wind up losing it?  Accord, Sphere, there's Parian on the smallest end of the scale\ldots''



``And you think there's some ugly twist to this.''



``Accord works out some scenario where it's possible to establish peace in Brockton Bay by exerting pressure in the right areas, promoting the right people, and allocating resources in the right way, but it turns out like a wish from a malevolent genie.  It turns ugly, or there's some loophole.  I think Tattletale should look at it.  That's all.  We need to be very careful.''



``You're obsessing over what Tagg said,'' Grue said.



``I'm trying to see everything through the perspective of what they'll be in a year or two from now, and maybe what they'll become ten years from now, if we're lucky enough to get that far.  What form will the team take?  How will the team run, and how will personalities change as time passes and we get more comfortable with where we stand?''



``There's time to figure this out,'' Grue said.



I frowned.  ``Not as much as you might be thinking.  Not nearly enough time.  The Undersiders need to solidify a hold on the city, become a \emph{fixture}.  It's impossible to do that by scrambling here and there and struggling to defeat each enemy that crosses our paths.  We needed a reason for the crazier and more reckless enemies to think twice before interfering with us.''



``People like the Slaughterhouse Nine, the Teeth.''



``And the Merchants, Lung and Bakuda.  All of them are very different kinds of villain, with a different sort of \emph{momentum}.  The Merchants weren't ever going to maintain a consistent hold on a territory.  It was less a question of whether they'd hold an area for years and more a question of the damage they'd do in the meantime.''



``You may be underestimating what they could have become.''



``Maybe,'' I admitted.  ``I get that the Merchants had the benefit of being the right people in the right place at the right time, but they didn't really have any sense of self-preservation.  There's going to be others like them.  I'm not underestimating \emph{that}.  There are teams who exist only because they earned attention through luck or circumstance, and those are the teams that \emph{have }to throw themselves at the biggest targets available.  They have to prove their worth to the world at large, or they collapse in on themselves.  Brockton Bay and the Undersiders are going to remain a target for guys like that if we can't create a big enough deterrent.''



Grue folded his arms.



``And here's the thing, there are ones like the Slaughterhouse Nine, too.''



I could see him react.  His arms dropped to his side, darkness trailing after them.  He seemed to realize he'd reacted, that he had nothing to do with his hands, and shifted his weight with his feet instead, leaving them dangling.



``Sorry,'' I said.



He shook his head.  After a second, he prompted me, ``The Slaughterhouse Nine.''



``There's the monsters who were drawn to the city because it was vulnerable, because others were already paying attention to it, or because it was \emph{different} in a way that appealed to their warped sensibilities.  We have to account for all these different people who are going to want to come after us and our city, and each demands a different response.  Can the Undersiders be boring enough to not be a desirable target to take down, scary enough to drive away the troublemakers, and still have the cold efficiency needed to take out ones like the Nine?''



``It's not impossible.  We're on our way there.''



``Except there's a whole other set of checks and balances in terms of the authorities.  Need to play along to a certain degree, cooperate, but also need to convey the right image.''



``A lot on your plate.  Are you going to be able to manage?''



I hesitated.



``What?''



``When I phoned you,'' I said, ``I wanted to talk about some things.  Two things.''



``And you wanted to talk in person,'' he said.



``In person,'' I agreed.  ``Um.  I guess I'm thinking about things in the same way Accord does.  Looking toward the future, accounting for the possibilities, simplifying.  If something happens to me-''



``Skitter,'' Grue said.



``We know something goes down in two years.  You know we live a high-risk lifestyle.  We're going to have enemies, I'll be risking my life.  I'm-  I guess what I'm trying to get at is that there's no guarantee I'll always be here.  I need to know if you think you'd be up to taking over.  Becoming leader again.''



``I couldn't do what you do,'' he said.



``What's the alternative?  Tattletale has her hands full with just the management side of things.  Imp?  Regent?  Rachel?  That's a disaster waiting to happen.  Do you really want the team to work for \emph{Accord}?''



``I don't see it happening.''



``No.  I'm just\ldots let's look at what happens in the future.  If you had to take over, could you?''



``No,'' he admitted.



``Okay,'' I said.



We stood there for a while.  I reached out and took his hand, my fingers knitting between his, the oily darkness slithering against my bare arm.  We stared up at the portal-tower, backed by an increasingly overcast sky.  So much depended on it, but we wouldn't hear the verdict for a little while yet.



``I raised the idea of you maybe getting therapy,'' I said.  ``I could use it too, to be honest.''



``Yeah,'' he said.



``Do you think, maybe, if you were in a better head space, you could handle the leadership thing better?''



``I don't know,'' he said.  ``Maybe.''



``Would you be willing to try?  I don't want to guilt you into it, but it'd give me a lot of peace of mind, knowing that you'd be there to keep things going.''



``I'd be willing to try,'' he murmured, his voice a hollow echo from within his darkness.   ``But why are you being so fatalistic?''



``I don't think I'm being fatalistic,'' I said.  ``But\ldots but maybe I sort of lost one half of my life.  I lost Taylor, not so long ago.  So I'm thinking about what happens if the other half were to disappear, too, and that's in conjunction with my focus on the future, on the team\ldots''



I trailed off.  It sounded feeble, but he didn't call me on it.



``Regent and Imp,'' I said, stopping when he turned his head my way.



A heavyhanded way of changing the subject.



``What about them?''



``They're together,'' I said.  ``I don't know if it's romantic, but\ldots they're together.''



``I'm aware,'' he said.



``It's a problem.''



``It is,'' he agreed.  ``But there's nothing I can do about it.''



``Rein them in?''  I suggested.



``How?  Aisha bucks at rules and restrictions.  She'd use her power and run before I could talk to her more seriously.  She was always one for flight more than fighting.  Fitting that she got that power.  Infuriating.''



``Then talk to Regent.''



``Not much better.  He's never one to face confrontation, but he handles it differently.  He doesn't \emph{run}, he evades.  He'd say or do whatever it took to stop me lecturing him, stop me from threatening him, and he'd go right back to what he was doing, in a different way, a different angle, so I'm less likely to catch on.  And if I angered him, or upset him, he'd make me answer for it somehow.''



``I don't think I've really seen him angry or upset.''



``You don't,'' Grue said.  ``Because he doesn't show it.  I don't think he even fully realizes it, that he feels that way.  But his jokes get a bit more barbed, he pushes \emph{back} a little harder when pushed.  He makes dealing with him annoying or toxic in a thousand small ways, until you can't continue to press him.  Then he uses that, goes right back to doing what he wanted to do.  It's not worth the trouble.  They're friends.  I don't like it, but I can live with it.''



``He controlled her.''



Grue let go of my hand, stepped away so he was facing me.  ``What?''



``He controlled her.  She let him, because she thought it would be interesting.  It made a difference in us winning against Valefor, yesterday, but\ldots I thought you should know.''



Grue didn't respond.  He folded his arms, so I at least knew he hadn't gone catatonic.



``Maybe they're not romantic \emph{now},'' I said, ``But who knows where they'll be a few years from now?  Their trust is born of mutually assured destruction, because neither can absolutely control the other, but it's still trust.  It could go places.''



``I'll talk to him,'' Grue said, and there was a hint of a growl in his echoing voice.



There was a distant rumble of thunder.  Surprising, given the amount of blue to the very north and south.  A summer storm?



Rain started to patter down around us.



In wordless agreement, we ventured to the staircase and into the building, to take shelter from the weather.



I reached up to my face to take my glasses off, ready to wipe them free of moisture, before realizing that I wasn't wearing them.  I let my hand drop.



Grue was looking at me, his expression hidden by his mask.  I felt momentarily embarrassed, then let the feeling drop away.



I reached up and pulled his mask off.  He let the darkness start to dissipate, his face half-hidden behind a veil of wisp-thin darkness, almost as if he weren't even aware I'd removed the mask.  He seemed pensive.



``Sorry to be a downer,'' I said.  ``Bearer of bad news.''



``It's not that,'' he said.  ``You've been looking forward.  That's good.  Except I'm wondering\ldots where are \emph{we}, in the future?  Suppose we made it through the end of the world.  Are we together in ten years?  Do we have kids?  Are we married?  Are we together, king and queen of Brockton Bay?  Have we retired?  Can you imagine a scenario like that?  Like any of that?''



I was caught off guard by the question.  I could visualize it.  Us in some mansion, little kids running around.  Just outside the window, Brockton Bay as it \emph{could} be, swelled with industry and life and vigor and development, nourished by that portal and all the promise the portal held.  Inside our home, a mess, not so different from the mess that I'd seen on first walking into the loft.  A \emph{good} mess, the kind of mess that came from life and living.  I could imagine Grue blanketing me in darkness to drown out the screaming, to give us a momentary privacy so he could hold me, kiss me.



\emph{Yes}, I thought.  \emph{Yes.  Please, yes.}



But I couldn't bring myself to voice the thought aloud.



``Me either,'' Grue said, his voice quiet, in response to an answer I hadn't expressed with anything but my expression and body language.



I couldn't lie and say that the mental picture, the \emph{fantasy}, was a real possibility.  I couldn't see it unfolding the same way I could see a thriving Brockton Bay secured with equal measures of fear and fairness.



It had been busy, hard and violent, with too much to do.  It was too easy to see how things could continue down that road.



Was it possible that this relationship could become something?  Yes.



Likely?  No.



``Shit,'' he said.  He must have seen something in my expression.  ``I should have kept my mouth shut.''



``No,'' I replied, shaking my head.  I put his mask aside on a workbench, along with the booklet Citrine had given us, reached out and plucked the folder and papers from Grue's hands, putting them aside as well.



Taking his hands in my own, I stepped close, pressing my body against his.  The bugs under my dress moved away from the points of contact so they wouldn't get squished, flying down and out of the way or crawling down my bare legs, making me very, \emph{very }aware of the bare skin of my legs.



He was cool, between the moisture-beaded fabric of his costume and the darkness, but if I pressed hard against, him, I could feel the warmth of his body where the darkness didn't sit between us.  I slowly, carefully drew his hands up so his arms were around my shoulders, arranging them.  When I was done, I wrapped my arms around his neck, felt him adjust his hold on me.



``Skitter- \emph{Taylor}.''



I had to crane my head up to kiss the tip of his chin.



It had been a fantasy.  Two damaged, lonely people clinging to each other for warmth in a dark time.  He'd needed a rock, I'd needed warmth and gentleness.



``There's no regrets?'' I asked him.  ``About \emph{us}, together?''



``No,'' he said, and his face was less than an inch from mine, his breath as warm as his power was cool.  I felt his chest rise and fall as it pressed against me.  ``It was right.''



\emph{It was right}.  Then.



``Then let's make this one place where we don't have to give any thought to the future,'' I murmured.  ``Focus on the present.''



He lowered his head and kissed me with surprising tenderness.



I hated to do it, but I broke the kiss, pulled away a fraction.  I murmured, ``Besides the usual precautions.''



``Mm,'' he murmured his agreement, an inarticulate, wordless sound that vibrated through his body and mine.





