





The rain had softened to a light drizzle by the time we finished.



My sundress was lying on the floor, a little worse for wear where I'd thrown it to the ground and used it to sweep much of the grit, plaster and sawdust from the spot where we'd laid down.  I shook it, then called my swarm, let my bugs crawl up my body to sweep and brush my skin clean.  The bugs made their way up the sides and back of my neck to my hair, then weaved through it as a mass, their bodies and mandibles helping to set it in order.  Others progressed down my arms, making their way to the dress, doing much the same with the fabric.



I was just about finished when I caught Brian staring at me.



I raised an eyebrow, and he smiled a little, shook his head, turned his attention to his costume.



I pulled the sundress over my head, and it was my chance to take a look at Brian.  He had only the leggings of his costume on, and was working one arm into the sleeve, his chest bare behind the `v' of the unzipped upper body.  The way his muscles shifted fluidly beneath his skin, the lines of his body\ldots I felt an ache that wasn't heartbreak.  A pang of loss on a baser level.



I \emph{wanted} him, damn it.  Wanted to nourish every sense with him.  The visual of him, the taste of his sweat when I kissed his skin, his smell, the bass of his voice and the little noises he made.  The feel of him, warm, the way every part of him was firm without being unyielding.



But no, it wasn't going to work out.  There was no long-term, and trying to cling to one would only spoil it all.



We hadn't said anything for a few minutes.  I didn't want to taint the silence with something that would only be awkward or ineffectual, couldn't think of anything meaningful to say, but I didn't want to leave him feeling like I was ashamed or unhappy, leaving it like this.



While he was still pulling on the upper part of his costume, I approached him, stood on my tiptoes, and then kissed his cheek.



Brian didn't respond as I got the bags, collected the paperwork, folder and booklet Citrine had given us and headed down the stairwell to the street, moving at something between a brisk walk and a jog every step of the way.



There were no catcalls as I made my way back to the upper end of downtown.  Many of the construction workers had taken shelter while the rain was heavier, moving indoors, and the ones who'd stayed outside were still in a state where they were focusing more on the work than on the wet, noisy, damaged world beyond the work site.



The thin drizzle of rain was bothersome.  It wasn't so much the wet, or the fact that it threatened to draw attention to me.  It was the fact that it was raining \emph{just} enough that it was uncomfortable, but I'd still look lame if I used an umbrella.



No matter, in the grand scheme of things.  I stretched as I walked, one arm over my head, one hand gripping it and pulling.  It was a good feeling.



For a while now, it had been hard to put a finger on my emotions.  What I was feeling \emph{now} was crystal clear.  Loss.  Disappointment.  Relief.



All things considered, I felt oddly upbeat as I boarded a bus and caught a ride to my territory.  I had to take off my hat to avoid bumping it into people, and felt conspicuous, the ends of my hair wet, hat gone, my light, tourist-y appearance a little the worse for wear.



I headed to the empty seats at the back, and I couldn't help but notice that one thirty-something year old guy was studying my face as I walked by.  He was with two or three of his friends, all of them tanned and dressed like the construction workers I'd passed.  Laborers.  I directed a small few mosquitoes to him as I brushed past.  One on each elbow and knee, to give me a sense of where he was moving and what he was doing.



It was thanks to the bugs that I could get the general idea of his movements: him reaching out to one of his friends, tugging on their arm, then leaning close to say something I couldn't hear.



Damn it.  Not a \emph{problem}, like it would be if someone spotted me on my way \emph{away} from my territory, creating the possibility that heroes might crash the meeting with Citrine, but nonetheless inconvenient.



I sat in the back corner and set the bags beside me.  They were loaded down with hostile bugs, I had the handle to the bus' emergency exit beside me, and my weapons were near-to-hand if things \emph{really} got ugly.



The four men approached me, and I kept looking out the window, feigning a lack of concern.



They sat around me, all well-built, tall men, a barrier between me and the rest of the occupants of the bus. The one who'd noticed me glanced my way; I met his eyes, and he gave me a curt nod before deliberately ignoring me.



I wasn't sure how to feel about that.  I appreciated the \emph{idea} behind it, assuming it was for my benefit.  Was it the notion that I was a girl who needed protection?  Or was I more bothered by the fact that I probably needed a shower, and they were sitting a little close to me?



It might help to get a license, I thought.  And a car.



I smiled just a little at the idea that I might get a Volkswagen Beetle.  It'd be stupid, impractical, and it would be too obvious.  A van would be better in every respect.



Not that I couldn't buy a number of cars.  A bug, a van, a boat\ldots even a helicopter, assuming Atlas wouldn't hold up.



No.  I was being unrealistic.  Still, it was an amusing thought.



Everyone exited the bus at the final stop, the area where the ferry had once been.  My self-styled escorts were among the last to leave, departing without so much as a glance my way, and I was last to step out into my territory.



I made my way deeper into my territory, my hat still stuffed in a bag, the soft rain wetting my hair and beading my skin.  My escorts made their way to a construction site, but other  people were recognizing me now that I was in my territory, and their recognition only helped others to notice.  Groups of people stepped out of my way in respect, in fear or a mingling of the two.



There was no rush.  I took a roundabout route, watching over my bugs and ensuring that everything was in an appropriate place.  Rats were still something of an issue, having feasted and multiplied many times over in the aftermath of the Leviathan attack, and I made a point of finding and exterminating any litters I found.



Mosquitoes had multiplied in the early spring, with shallow water everywhere for them to lay their eggs and multiply.  They were one species I wanted to keep away from people, and I made a point of moving them away from all residential areas.  They were the filler in my swarms, one of the only species around that I could eradicate or use up entirely without doing too much to upset the local ecology.



I wanted Brockton Bay stable, everything in order.  That wasn't limited to the human aspect of things.



I entered an area where the damage had once been heaviest, and where much of the construction had recently finished.  Here, things had been brought up to standards.  The roads were still wide, owing to the fact that this area had once been intended more for industry and the movement of big ships and trucks, and that had been preserved.  Even the alleys, marked clearly with new one-way signs, tended to be wide enough that trucks and cars could potentially pass through in pairs.  But where there had once been dilapidated warehouses and factories, the buildings were quaint, neat and tidy, with siding in whites and light colors.  `Seaside colors' I'd heard it described.  Colors that were warmer and more enticing, fitting with the boardwalk-in progress, the beaches that were being thoroughly cleaned, and the bay itself.  The water was gray now, reflecting the overcast sky above, but it was capable of being a brilliant, stellar blue.



People were already officially moving into this area, which had once been the part of Brockton Bay that people were urged to stay away from.  Couples, laborers, people with kids.



I felt a measure of distaste as I spotted a crude attempt at my `tag' on the side of one of the nicer, newer homes: a narrow, pale blue condominium.  I'd made requests that the graffiti be kept subtle, and I'd told people who worked for me to pass on word that others shouldn't take it on themselves to repeat the mark elsewhere, to limit confusion.  My emblem, a beetle with wings spread, marked walls and signposts, predominantly on the buildings that had yet to receive attention.  Still, there were crude replicas here and there.  I'd have to make sure someone was watching out for that and passing on the word.



People were still watching me, eyeing me as I walked through the area.  Mosquitoes I'd brought to myself were clinging to me, leaving little doubt about who I was.  There was no need to hide.  I'd have other measures in place before too long.



My detour brought me around to what had become a makeshift memorial.  There were flowers and the like forming a ring where a fence had been erected.  In the center of the ring, an oval shape sat embedded in the ground.  This was the area where we'd fought Leviathan.  A time-distortion grenade had gone off, and three heroes had been trapped inside.  Brockton Bay's own Dauntless among them.



The center of the bubble was as impenetrable as Clockblocker's power, while the effects were more nebulous around the edges.  Dust and moisture were caught in the sphere, obscuring the contents, all moving a fraction of a glacial pace.  There was a hand print at one point where someone had tried to touch it, shifting the dust and moisture, losing some skin in the process.  In other spots, less respectful people had thrown things at the sphere.  Pennies, sticks.  That had stopped when others had tidied up the area and the flowers had started appearing here and there.



There had been talk of blanketing the entire thing in flower petals, so it wasn't a gray-brown egg with a neat pattern, but others wanted to leave it be, protecting it with a bubble or shelter so the rain and dust could clear away, and people who visited could see the three heroes as they were when they were caught within, in the midst of being thrown through the air, the very moment they effectively gave their lives for the sake of the city and the world.



The entire thing was framed by the surrounding buildings.  There'd been too much damage from the skirmish with Leviathan for them to stand, and I'd made a special request to the designers for the rebuilding.  They were shaped so that there was something of a clearing around the bubble.  The city could decide what to do with the bubble itself; I'd done what I could with the surroundings.



I reached into one of the shopping bags, retrieving a small bouquet.  I laid it just outside the fence, where it joined innumerable other tokens of respect: Letters, flowers, an action figure, a Dauntless poster with something illegible scribbled on it.



The city was healing, but there were still scars.  Some were smaller, like this.  Others, like the appropriately named `Scar' downtown, or the lake Leviathan had created, weren't so minor, would loom in the awareness of the people who lived here for a long time to come.  The `Scar' had been encased in a squat, windowless, zig-zagging piece of architecture.  The lake would likely remain as it was, until the city found a way to make more use of it.  Neither was particularly pleasant to think about, either in terms of what had happened or the ideas about what could come in the future.



I could only hope that we could be so lucky in other areas, to have only scars and unpleasant reminders.



I was halfway back to my lair when I sensed intruders.  In an instant, my nerves were on edge, bugs stirring from the surroundings to investigate as discreetly as I could.



I thought of Leviathan attacking the area, of Mannequin's visits, of Burnscar.



Except these were heroes present.



I let myself relax a fraction, waited until I was as calm as I could get.  Then I approached.



Parian was sitting on a bench under some eaves, Miss Militia leaning against a wall a few steps to her right, holding a bottle of water, and Flechette was a little ways away, staring up at a building in progress.  My people hung back, staring or watching the heroes with a wary eye, hesitant.  They couldn't be sure if there was a confrontation in the works or if they should keep working, so they weren't leaving and they weren't really working.



Others were staring at me, \emph{noticing} me.  Miss Militia seemed to catch onto the reaction of the crowd even before I was in her field of view.  She straightened and a rifle appeared in one hand.



Flechette saw the heroine move out of the corner of one eye, turned my way with her arbalest in hand.



Neither of them pointed their weapons at me.  A good sign.



``You're in my territory,'' I said, when I was in earshot.



``Apparently,'' Flechette said, her voice level, ``We can't go anywhere in this city without being in \emph{someone's} territory.''



Miss Militia shot the girl a warning look.  ``Parian invited us.''



I glanced at Parian, who was still sitting in her seat, a cloth doll in her lap.  ``I would have preferred if she'd asked me first, but fine.''



``We wanted to talk,'' Miss Militia said.



``Yeah,'' I said.  ``Because that's worked \emph{very} well in the past few days, hasn't it?  Or did you miss the notice?  The PRT outed me.''



``I'm aware,'' Miss Militia said.  ``I was there when they made the decision.  I spoke against it, for all the good it did.''



``For the record\ldots'' I said, and I let bugs crawl from beneath my dress to progress along my arms and legs, up my neck and around the edges of my face.  I didn't have my costume, but I could use intimidation to armor myself.  ``Your stay here is a \emph{very} temporary one.  I can ask you to leave at any time.  Your choice whether that's peacefully or if I evict you.''



I could see Flechette tense.



``We're not looking to fight,'' Miss Militia said.



``Good,'' I said, glancing around me.  The rain was still pattering down around me, and the street was damp, not \emph{flooded}, but it wouldn't be good to offload my bags there.  I ventured under the eaves and set the bags down in a dry spot.  I folded my arms.  ``Give me your weapons.''



``There's no point to giving you mine,'' Miss Militia said.  ``I could call it back to me, switch it to something else and shoot you before you could react.''



``That's fine,'' I told her.  ``This is a symbolic gesture.  Please give me your weapons.''



She stared at me, taking me in.  Then she looked down at the gun.  It flickered and became a bowie-knife.  She tossed it into the air, caught it by the flat of the blade, and then approached me, extending the handle in my direction.



I took the blade, and I could swear it reacted, vibrating.



``It's alive.''



``Yes,'' Miss Militia said.  ``It's a part of me.''



\emph{A part of her, as in\ldots a part of her mind? Or is it her passenger?}



I felt like there was something more I should say in response to that, but I decided to focus on the matter at hand. People were watching from the sidelines.



``Flechette.  Your arbalest,'' I said.



She looked far less agreeable than Miss Militia had been.  She glanced at her superior, received a nod in response.



Flechette placed the arbalest on the ground halfway between us, then backed off.



I was willing to bet she had other weapons, but it wasn't worth the effort to get them from her.



``You owe me,'' Flechette told Parian.  Parian didn't respond, staring down at the ground.



``She owes you?'' I asked.



``I was \emph{home}.  I came back because she asked, and it's probably coming out of my time off.  And you weren't even here when we arrived.  We waited twenty minutes.''



``I would have been if I had any notice,'' I said.



``I don't want something ugly to happen on my vacation day,'' Flechette said.  ``That's all I'm saying.  Not happy-cool about this as it is.''



``Were you shopping?'' Miss Militia asked, as if she were trying to change the subject or distract me from Flechette.  When I looked, her eyebrows were indicating mild surprise.



``I can't go shopping anymore,'' I said.  ``I don't want to sound hostile, but reminding me of that isn't going to help anything.''



``You're upset,'' Miss Militia said.  Before I could think of a retort, she added, ``You deserve to be.''



I shut my eyes briefly.  When I asked my question, I sounded almost exasperated, ``Why are you here?''



``The first reports came back from inside the portal, and they're promising.''



I nodded.



``Fresh water, lumber.  Geological surveys suggest there's mining, and that's all in close proximity to the portal.  Plant, animal and insect life seem to have evolved in rough parallel to our own.  Worldwide, there's few signs of pre-existing human civilization, and no human life that we've been able to detect.  The deviation point seems to be nearly five thousand years ago.  Several teams are working on analyzing the sites where humans settled, looking for the cause of extinction.  We'll have reports back soon, and we expect to make a statement to the world at large in a few days.''



``That's good to know,'' I said.  I didn't mention that Tattletale had her own teams present.  If she weren't nursing a bad migraine, I suspected she would have already informed me of the details.



``Even if it turns out there's a plague, parasite or hostile agency in this other world, the sheer value of the resources on the other side are going to make this portal very valuable.  I think it's safe to say Brockton Bay stands to become a rich city, and that begins the moment the news gets out.''



I nodded slowly.



``You don't look surprised.''



``Expected something like that,'' I said.  ``I suppose this means you want to talk to the villains that are currently controlling this soon-to-be-rich city's underworld.''



``Dragon and Defiant came to Brockton Bay with the interest of setting up a plan, drawing a truce between your group and ours.  I suspect Dragon already had suspicions about this other world and everything it entailed.''



``Except things got screwed up along the way,'' I said.



``Yes.  And on the other side of things, particular events came to light, validating things you'd said, on several fronts.''



I glanced at Flechette.  I'd given her directions to find the armband.  There was also the business with the leading heroes of the Protectorate being complicit in the Cauldron debacle.  I wasn't sure Flechette was up to date on that one.



``You checked out the armband?''  I asked Flechette.



It was Miss Militia who answered, ``I was informed about possible tinker material being passed around and investigated, possible contraband.  It was Flechette investigating the device.  We contacted Defiant together and got the answers we were looking for, in a much more direct manner.''



``He was your friend.''



``A colleague and a friend, yes.  We were very good at different things.  He told me he was sorry he couldn't attend this meeting.  He's\ldots preoccupied at present.  Flechette, Defiant and I had a long series of discussions that led nowhere in particular.  It only pointed to an increasingly ugly situation without an easy resolution.  Until Parian contacted Flechette about a meeting.''



``With me,'' I said.



``With you.''



I glanced back at Parian.  She wasn't moving, still sitting in a chair, not looking our way.



``Okay,'' I said.  ``We can talk.''



``Good.  Let me start off by extending an apology.  I'm sorry things turned out as they did.  I don't agree with the way that incident played out.''



\emph{That incident}.  The thing at the school.



``We looked back at what happened with your history at the school, the allegations of bullying--''



``Stop,'' I said.



She did.



``If you're going to say anything on the subject, don't mince words.  You know who Shadow Stalker was beneath the mask.  You probably have an idea of the kind of things she did.  Don't pretty it up by using words like \emph{allegations}.''



Flechette stared at me.



``Not allegations then.  The bullying, the abuse you endured.  I don't like that it happened.  I don't like that we were complicit in it.  It fills in quite a few blanks, helping me make sense of what happened after you uncovered Shadow Stalker's secret identity.  Defiant knows too, now.  I recognize that it might even have pushed you to take a different direction with your newfound powers.''



``I got my powers because of her,'' I said.



Miss Militia fell silent.



``Early January, followed by a hospital stay.  You can look it up.''



``I'm sorry,'' she said.  ``I suspected it was your mother's passing that caused your trigger.''



``See,'' I told her. ``There's one thing that's really grating with you heroes.  You keep saying \emph{sorry}.  Oh, you guys are sorry your top members were kidnapping people and turning them into freaks.  You guys are \emph{sorry} that some of your members bought their powers.  You're \emph{sorry} that your bosses crossed a line, trying to drop bombs on our team members after we did the grunt work of facing the Slaughterhouse Nine.  You're \emph{sorry that }you went to such extremes to rehabilitate your group's sociopath that you let her get away scott-free with the abuse she was inflicting on a bystander.  But you don't change.  You don't \emph{do} anything about it.''



There was enough venom in my voice that Flechette had started eyeing her arbalest, where it sat in the rain.  One of her hands was poised in the air, as if she were preparing to reach into a pouch at her side.  She was looking at the crowd around us, and I couldn't tell if it was because she was worried they'd respond if she attacked me, or if she was double checking they were out of earshot.



``That's why we're here,'' Miss Militia said, calm.



``That's why we're here,'' I echoed her.  ``Yeah.  Well said.  All those events I just mentioned, they're part of why \emph{I'm} here.  I'd say you have nobody to blame but yourselves for the fact that you have \emph{me} to deal with, but I'm willing to admit I'm largely at fault for the decisions I made.  You guys\ldots you just greased the wheels, I suppose.''



``We'd like to change that dynamic.  Defiant, Dragon, myself--''



``You want to change, but you're still working for \emph{them}.  For the Protectorate,'' I said.



``We have to.''



I frowned, forced myself to relax.  ``Dragon said the same thing.  Tattletale filled me in on the reasoning.  You think we \emph{need} the Protectorate.''



``We do.  And if everyone with enough of a conscience to feel regret over these events were to leave, I don't think anyone will be happy with the group of those who stayed behind.''



``There's another route,'' I said.  ``Accept that it's broken, accept that it needs to change, and \emph{do} something about it.  Recognize that what Tagg did was fucked up, \emph{act on that}.''



``It's dangerous.  Things are sensitive.  There's only an eighteen percent chance of success in the upcoming fight if we face Behemoth.  Twenty-nine percent if it's the Simurgh, with\ldots a great deal more fallout after the fact.   Without the Protectorate, chances drop to an even lower number than they are, and the damage gets worse.''



\emph{Dinah}.  The only way they'd have these numbers would be Dinah.



``You're afraid of rocking the boat when the ship's sinking,'' I said.



``Something like that.''



I sighed.



``But\ldots'' Miss Militia hesitated.  ``In light of revelations over this past month, keeping recent events in mind, and perhaps because we have more of an insight into who \emph{you} are, Taylor Hebert, I think we might be more open to more discussion than we were.''



``Who's \emph{we}?''



``The Protectorate, the Wards.''



``The PRT?''



Miss Militia shook her head.



It wouldn't be enough if the PRT wasn't on board.  There was some argument I wanted to make, something I wanted to say, but I couldn't articulate it, couldn't quite form the thought in my head.



``What do you think of this?'' I asked Flechette, to buy myself time to think, or maybe in hopes of rounding out the half-formed thought.



``It doesn't directly affect me,'' she said, glancing away.  ``I'm still trying to decide if I should trust you\emph{.}''



``If it doesn't directly affect you, why does this matter?''



``Because I got home and saw my family, and they said I was different, \emph{angrier}.  And they were right.  Because I'm hearing about everything that's happening, all these secrets coming out, and I can't even look at my teammates without wondering if there's something nefarious about them.  Because Parian was the one good thing I found in this city, and you \emph{recruited} her,'' Flechette said.



Parian looked up.



``That costume, it's like a slap in the face.  Like, it wasn't obvious enough you corrupted her.  You had to take the playfulness away?  The joy?''



``Hey,'' Parian said, standing.  ``It was my decision.''



``She was following advice I gave,'' I said.  ``She wanted to stand up to the people who are trying to attack her territory, and she wanted to do it without \emph{our} help.  Being a little more intimidating doesn't hurt.''



``You--''



``Flechette,'' Miss Militia cut her off.



Flechette went limp, the fight gone out of her, just like that.



``I don't know anymore,'' Flechette said.  ``I don't know where I'm going.  Everything was all laid out, a career with the Wards, a career with the Protectorate.  Except I'm not even sure there's going to be a future anymore\ldots and I'm not sure what happens if there is.''



``I think you and I are very similar on that front,'' I said, my voice quiet.



She looked at me, her lips pressed together in anger, then looked away, unable to disagree, as much as she might want to.



``I guess\ldots I guess what it comes down to,'' I said, ``Is that you have to decide what you want.  What you're willing to fight for and make sacrifices for.''



Flechette's eyes flickered over to Parian, then down to the ground.



\emph{Ah}.



``I'm\ldots alone,'' she said.  ``I've never been alone, never been good at being by myself.  Last few days I was here, I wanted nothing more than to go home.  And when I finally got to\ldots I've never felt more disconnected from everyone around me.  It wasn't what I wanted, or what I needed.  I can't trust my team, can't talk to my family, can't confide anything in my friends.  Sounds stupid when I say that.  Sounds \emph{weak}.''



``I'm fully aware I don't have much stock with you, so maybe what I say isn't worth much to you, but I don't think less of you for saying that.  The prospect of being all on your own is scary.  It's \emph{harder}, and things are hard enough as it is.''



Miss Militia was staring at me.  I met her eyes.



``Interesting to have a conversation with you,'' she said, ``With a greater understanding of the girl behind the mask.  What do \emph{you} want, Taylor?''



``I'm not Taylor,'' I said.  ``In costume or out, I'm Skitter, up until I decide on a new name.''



``Skitter, then.''



``Compromise,'' I said.  ``Give me compromise.''



``I can try.''



``You can, the Wards can, but the PRT won't.  You said as much.''



``They have other burdens to bear.''



``And until they work with us, they're going to be a bucking bull in a china shop,'' I said.  ``Strutting around and doing catastrophic damage to a delicate situation.  Tagg said this is a war--''



I could see a look flash across Miss Militia's face.



``--and you can't reason with people like that,'' I said.  ``Not people who are hungry for conflict, willing to fight until \emph{someone's} too beat up to fight back.''



``No,'' Miss Militia said.  Her tone of voice had shifted.  ``You can't.  I've heard him say something along those lines before.  A small part of the reason I'm here.''



``Then you agree.  He can't be leading the PRT if we're going to reach any kind of consensus.''



``I can speak to some people, but I don't think I'll be able change anything.  The very structure of the PRT is \emph{built} around the idea that the unpowered call the shots, and the capes follow them.''



``We both know that it's not that cut and dry,'' I said.  I glanced at Flechette.  Did she know about Alexandria?



``I'm sorry,'' Miss Militia said.  ``It's not in my power.''



``It's in mine,'' I said.  ``I think.  I hope.''



I could see the furrow in between her eyebrows.  ``What are you thinking?  More violence?  You won't be able to twist Tagg's arm to get what you want out of him.''



``I'm still not entirely sure,'' I said.  ``I think I \emph{can} twist his arm.  It'll be easier if you're willing to compromise.  I need your help to make this work.''



``What sort of help?''



``A mixture of support and passive resistance.  Nothing that hurts the PRT as a whole.  Nothing that hurts the result against the Endbringers.''



``Okay,'' she said.  ``Specifically?''



``For starters, we treat every situation like you treated the ABB, back in April.  We address threats, tag team them.  Only we communicate more this time around.  The Teeth are a problem, but others are going to arise when word about the portal gets out.''



``Done.  The PRT may not play ball, but we can communicate by other channels.''



``The heat's off the Undersiders and Ambassadors both.  We can't do anything constructive if you guys are after us.''



``The PRT will continue to order us to engage you.''



``Fine,'' I said.  ``Then that's when you apply passive resistance.  You return to your bosses and you say the mission against the Undersiders was unsuccessful.  Bitch ran, Grue used his darkness, Tattletale must have passed on information.  We do our best to avoid giving you cause to come after us, you don't attack when the bosses order you to.''



She frowned.  ``This is giving you amnesty for past misdeeds, in practice.''



``Yes.  But it ensures we're \emph{all} in fighting shape when the next Endbringer fight goes down.''



``Accord remains a problem.''



``We'll keep him busy, put him in the background.  Tattletale has a sense of his motives.  We can keep him occupied while keeping him from having a direct hand in things.''



``Our passivity would hinge on his.''



``Deal,'' I said.



``And you can't keep pushing things like you have been.  The degree of aggression you've been demonstrating, with the attack at the PRT head offices and Valefor, it tests our patience.''



``They noticed, then?  Valefor's eyeballs.''



``That's the kind of event that provokes a response from the PRT.''



I nodded.  ``It's supposed to, just a little.  It was a message to Tagg as much as a way of dealing with Valefor.''



``It's not the sort of thing that will get him to abandon his position or back down.''



``I think it is,'' I said.  ``But that's only one aspect of a greater plan.''



I could see her frown.  Not that I could see the lower half of her face, but I saw it in her eyes.



``A day or two,'' I said, ``Then I stop.  I'll fill you in on the details as soon as I have them.''



She frowned.



``Flechette,'' I said.



``What?''



``Is this satisfactory?  If we call a truce, the local heroes will be free to assist Parian.  I suspect she'll be willing to accept their help where she's less accepting of ours.''



``I will,'' Parian said.



``Would that make things easier between the two of you?''



``I'm not local,'' Flechette's words were a whisper.



``You could be,'' I told her.  ``Or you could visit.  I can't do a lot, but I can maybe help give you your friend back.''



``We can use all the help here we can get,'' Miss Militia said.  ``If you wanted to join the Wards team on a permanent basis, I could see about arranging something.''



``Let- let me think about it,'' Flechette said.  ``It'd mean leaving my family.  Or moving them, depending.''



``Then that's as settled as it's going to get,'' I said.



``I still have concerns about your continued swathe of destruction,'' Miss Militia told me.  ``If your vendetta against Tagg gets any uglier, this idea won't hold.''



I'd hoped the distraction of talking to Flechette would keep her from returning to that topic.



``Give me the benefit of the doubt,'' I said.  ``Please.''



I could see the lines around her eyes deepen as she frowned.



``Just this once.  It's all I've been asking you guys for, from the beginning.  Trust that I'm doing what I'm doing for a good reason.  I just need you to maybe turn a blind eye here and there, support me when the situation calls for it.  I'll fill you in where I can, and I'll make a leap of faith and trust that you'll know what to do otherwise.''



``Okay,'' Miss Militia conceded.



A second passed with nobody speaking.



``I'd extend my hand for you to shake,'' I told her, ``But we probably don't want something that blatant popping up on a cell-phone video.  For now, at least, this truce stays unofficial.''



She offered me a curt nod.  I held her knife out towards her, and it dissolved into a mess of green-black energy.  It zipped to Miss Militia's hand, became a pistol.  She holstered it.



Together with Flechette, she left, making her way out of my territory.  A hundred pairs of eyes watched them leave.  Maybe I could pass word around to get people to keep quiet on the subject.



``Thank you,'' Parian murmured.



I glanced at her.



``For what you said to Flechette.  How you said it.''



``I have more respect for you than you'd probably believe,'' I told her.  ``I hope it works.''



``I think it will.''



I watched the heroes as they departed.



``I'm going to take a shower,'' I said, eyeing the light rainfall beyond the eaves of the building.  I shrugged, heading towards my lair.  ``Redundant, maybe, but I think a shower is the \emph{least} of the luxuries I'm entitled to as a wealthy, nationally recognized supervillain.  I'll talk to you later.  Let me know if you hear back from Flechette.''



``I'm sorry,'' she said, to my back.



I looked back, gave her a quizzical look.



``I could have arranged that better,'' she said.  ``I sprung it on you.''



``No,'' I shook my head.  ``It was necessary.  No worries on that front.''



I didn't voice my true thoughts aloud, though.  The conversation with the heroes had needed to happen.  The fact that Parian and Flechette had been present was a stroke of luck.  The downside, the other side of the matter, was that I now had to act before someone in a position of power caught on to what was happening with our truce and ended it prematurely, or before Miss Militia herself reconsidered.  I had to act before \emph{I} started having second thoughts.



Which was harder than it sounded, because I hadn't even figured out if there was a way to pull this off without alienating everyone that counted.



Parian had inadvertently accelerated my plan. For that, I hated her, just a little.  That feeling was clear enough, small as it might be.





