





\emph{Hate to do this with the weather like this, }I thought.  I thought about the meeting Parian had arranged with Miss Militia.  \emph{But my hand is being inadvertently forced.}



One more step forward.  One more phase in the plan.



The wind was worse than the rain.  I had to wonder how much of it was the aftermath of the Leviathan attack.  The city had been flooded, and those same floodwaters had evaporated into the air, trapped within Brockton Bay by the surrounding trees and hills\ldots how wide-reaching were the effects of that one incident?



The downpour was steady, moderate.  The wind was what turned it into a barrage, a persistent pelting of droplets that moved horizontally as much as it moved vertically.  The \emph{noise} of it, tapping against my armor and lenses, made for a steady patter.  My bugs were lurking and gathering in spots where there was shelter, and where things were dry.  With only the light of the moon above, these were the same areas that had shadows, by and large.  The masses of bugs only seemed to give those shadows substance, made them seem deeper, through the masses of dark brown, gray and black bodies.



Through other bugs I felt the movements of the wind, felt how it formed eddies, curling into itself when it met with dead ends, large or small.  I could, with a small number of bugs, feel how strong and steady the gale was where the buildings weren't tall enough to break it up.  They helped me track the others around me, through bugs that took shelter in the drier folds of their costumes.



The Undersiders were here.  Minus Tattletale, we were all standing in the street a distance away from a squat building.  Regent was off to one side, ready to trip up our enemy if they made a sudden appearance.  Rachel hung back, corralling her forces, while the rest of us watched the building for any hint of trouble.



But Grue stood next to me.  I appreciated his presence, his \emph{casualness} in light of the way we'd effectively parted.



I could sense the Ambassadors.  Citrine and Othello were there.  So were four new recruits: Jacklight, Ligeia, Lizardtail and Codex.  The fifth potential recruit hadn't been so lucky.  The four of them stood off to one side, in the shelter of Citrine's power, listening as she gave instructions.  The area around them was somehow faded in terms of the colors there, the area she was affecting looked as though I were viewing it through colorblind eyes that were capable of only seeing yellow.  Water wicked off of them as though they were waterproof, leaving them utterly dry even in the wind and rain.



Lizardtail's power was pressing against me, even from the other side of the street.  It penetrated my costume to the skin, making my skin tingle and ensuring that I was always aware of where he was.  It was like the sensation of standing in front of a fire, just close enough to feel as though that heat had a physical form, just close enough to be bearable.  It wasn't hot, though.  It was cold, if anything.



The rest of our forces were marshaled throughout the area.  A handful of volunteers from my territory, surviving members of the O'Daly family, had made their way to rooftops, stood at the ready with walkie-talkies and binoculars.  They'd have to make up for the fact that my bugs weren't as mobile in this weather.



Tattletale's mercenaries were here, though she was still largely incapacitated.  Minor, Brooks, Pritt, Senegal, and Jaw.  Regent had two followers, and I was doing my best to avoid paying attention to them.  It wasn't the time to investigate whether he was controlling people or legitimately hiring them.



Rachel's underlings were present too, hanging back enough that they were out of sight of the building.  Biter, Barker, the veterinarian, the boy with the eyepatch, others I didn't recognize: a young teenager with darker skin, a tall man with a broad belly.  Each of them held a chain -the tall man and Biter held two- and each chain had a dog harnessed on the other end of it, grown to a fair size by Rachel's power.  Only Bentley and Bastard were full size.



Inside the building, the Teeth were recuperating from a recent conflict with Miss Militia and the other heroes followed soon after by an attack from Parian's stuffed animals. As a whole, the Teeth amounted to twenty or so unpowered troops, plus a half-dozen or so powered ones.  Even the unpowered Teeth had `costumes' of a sort, were dressed in a hodgepodge of armor that made it hard to tell them apart from the powered members.



As a whole, they were bandaging minor injuries, preparing food, talking, joking, relaxing.  There were two televisions on, each playing something different, volume turned up, and the noise was discordant, even to the muted, confused senses of my swarm.  Porn on one television, I was pretty sure.  The other channel was either a cartoon or a news broadcast, judging by the words I was able to hear.



There was a fight in progress, a duel, between two unpowered members.  One was getting the better of the other, pounding his face in while others jeered and laughed.



One of the female members of the Teeth, I suspected Hemorrhagia, was cooking food for her team.  A distance away, Butcher was sitting on a stool, her feet up on a table, her mask off.  She had a cloth in hand and was wiping her gun clean, oddly disconnected from the clatter and chaos of her team.



I supposed the thirteen other voices in her head kept her company.



It had taken time to analyze them, to assess what each of the Teeth were doing and make a note of every individual part of it.  To do it discreetly, with no more than the bugs that were already in the building.



The Ambassadors were patient.  I got the sense that they could have waited for two hours in this wind and rain, and their only concern would be that their clothes and hair were a little worse for wear.  My teammates were a touch more restless.  Rachel moved from dog to dog, enforcing her authority, keeping them in line, and making sure they were listening to the underlings.  She was putting her trust in me, but I could tell she was getting tired of this.  Tired of the minutes passing with nothing happening.



Regent, too, was reacting.  He was maintaining a running commentary on everything from the weather to the surroundings, our allies and \emph{me}.



``And\ldots twenty minutes in, the rain's still pouring, the wind's still threatening to drop a house on our heads, and we're \emph{still} not doing anything.  I think our fearless leader needs to remember that \emph{some} of us aren't as good at being imposing when we're drenched and standing around in the dark.  \emph{She }does that whole schtick where being gloomy and creepy only make her scarier.  You know how scary \emph{I} am with a wet shirt clinging to me?''



``Shut up, Regent,'' Grue said.



``I'm just saying.  She could be more considerate.  Maybe \emph{we} could wait indoors, and \emph{she} could stand out here in the rain, using her power to investigate our enemies.  If she's even using it.  Maybe she fell asleep standing up.  Been a hard week for her-.''



``Regent,'' I said.  ``Be quiet.''



``She's awake!  Excellent,'' Regent's jovial tone was forced enough to border on the sarcastic.



``There are no vantage points that are also indoors,'' I said.  ``I'd bet that's why Butcher chose that building.  The parking lot that surrounds it, the terrain, it's all to her benefit.''



``So we pick a \emph{mediocre} vantage point.  Or a shitty one.  So long as it's dry.  Or, here's an idea, maybe we \emph{attack}.  We have them outnumbered, we have better powers than most of them-''



``We win absolutely,'' I said.  ``Or we don't fight at all.  Too many of them have powers that could help them escape.  Vex fills an area with her power and runs, Animos transforms and runs, or Spree masks their retreat with his power.  This way, we take\emph{ }\emph{all} of them down, or we at least affect them on a psychological level.''



``Then why don't we have them surrounded?''



``Because we don't need to,'' I said.  ``Keeping Butcher from picking us off is a bigger priority.  We do that by forming battle lines.''



``Huh,'' he said.  There was a pause.  ``Twenty \emph{three} minutes, standing in the rain\ldots''



Inside the building, Hemorrhagia called out, ``\ldotsst ready.''



The Teeth collectively began to make their way to the kitchen, while Spree headed for the washroom.



There.



``\emph{We're attacking},'' I said, and I spoke through the bugs that were near each of my allies.  ``\emph{Be ready}.''



The bugs I'd kept in reserve swept into the building, not from the direction our forces were standing, but from the opposite direction.  They flowed in, swarming over the Teeth.



Less useful bugs plunged themselves into the food.  They scattered money, where money was left out in the open, caught unattended weapons and pieces of armor and either buried them or started to drag them from sight.



``No!'' Hemorrhagia shouted, trying to cover her chili with a lid,  ``No, no, fuck you, no!''



Hearing the shouting, Spree stood from the toilet, only to find a handcuff connecting him to the towel rack.



``Fight!'' one of the Teeth shouted, rather unnecessarily.  He was joined by others.  ``Kick their asses!  Kill them!''



Spree managed to tear the towel rack from the wall and made his way out of the washroom, working to get his belt buckled, other armor gathered under one arm.  I was well aware of how costumes made using washrooms a pain in the ass on the best of days: getting everything necessary off, getting it back on again, attaching everything essential\ldots Spree had the added issue of innumerable trophies and pieces of armor in his suit, all loaded down with spikes and hooks, and he was now in a rush, running forward into a swarm of biting, stinging insects.  He dropped one piece of armor, and bugs swarmed it.  He cast one backwards glance at the item in question, an elbow pad or knee pad, and then decided to leave it behind.



It was the little things that would deliver a hit to their morale.  Attacking while they were tired, spoiling a meal they were anticipating, throwing everything into disarray.  If they happened to come out ahead in this fight, or if any of them slipped away, they might return to reclaim their things, they'd find cockroaches had chewed through the cords and internal wires of their televisions, that pantry moths infested their food supplies, and every article of clothing was infested with lice.



And if they entered this fight \emph{mad}, all the better.  It would mean they were gunning for us instead of running.



The first person out the door was caught by a tripline of spider silk.  Others trampled over him.  One fired a gun into the darkness beyond.



Wrong door, wrong end of the building.  And the door had somehow closed and locked behind them.



The powered members weren't in that group, though.  As disorganized as the rank and file members were, the capes in the gang were only looking to their boss, gathering in the kitchen.



Butcher didn't react as bugs bit and stung, and capsaicin-laden bugs found her eyes and nose.  Her skin was too tough, and she didn't feel pain, thanks to Butcher twelve's powers.  She was \emph{composed} as she lifted a gun that would normally have been mounted on the back of a truck.  Without putting it down, she held it with one hand and donned her mask.



She turned our way, as though it wasn't even a question.  A sensory power.



\emph{Butcher two, the ability to see people's veins, arteries and hearts through walls.}



She had the powers of thirteen capes, watered down, plus her own.  Some of those capes had possessed multiple abilities.  By power or by cunning, each had managed to kill the last.  \emph{This} Butcher had the resources of each of them.



She led her group through the doors towards us, as silent as they were noisy.  I'd almost expected her to do the inverse of what she was doing and send her foot-troops in first.  Instead, she was the first through the doors, her powered allies immediately behind her.  Her foot troops were last to arrive, traveling around the full length of the building, swearing all the way.  They filled in the gaps of her group and gathered behind.



It was a different dynamic than some groups we'd fought.  These weren't loyal soldiers or people fighting because they had nothing to lose.  They were opportunists, riding the coattails of the ones with the \emph{real} power, hyenas picking at the scraps that were left behind after the lions had supped.



Spree was the first to use his power, and I got a sense of just how and why the group had arrived at this present strategy.  It wasn't just that Butcher was dangerous enough to walk face-first into danger.  They had Spree to form their front ranks.



Four Sprees split off from him as he stood there, slightly hunched over as if bracing himself against recoil.  They were produced with such force and speed that they briefly flew through the air, stumbling slightly as they hit the ground running.  Three more Sprees were a fraction of a second after the first wave, with even more following a half-second behind \emph{them}.



Fifteen or so Sprees in three seconds, before I'd even had a chance to call out an order.  Duplicates produced at the rate that a machine gun spat bullets.



They ran, some screaming, others swearing aloud as they closed the distance between our two groups, charging as a mass, limbs flailing, weapons-



Weapons?



It was hard to see in the rain, but the Sprees were all subtly different.  Some had knives or pipes they could bludgeon with, others had guns, and more had improvised weapons.  The mixing and matching of their armor was different as well.



There was a drawback, though.  Whatever they were, as solid and innumerable as they might have been, they were dumb, getting dumber every second they were alive.  He was producing a living tide of bodies, but they weren't \emph{capable}.  They were good for little more than sheer body mass and violence.



By the time the first ones reached us, they were barely able to put one foot in front of the other.  One reached me, swung a table leg at me in a wide, predictable swing.  I caught it, twisted his arm, and pushed him into a Spree that was stumbling forward from behind him. They both fell, and neither seemed to have the wherewithal to climb to their feet before they were trampled underfoot.



It was like fighting an infant with the size and strength of a grown man, except there were fifty or sixty of them.  A hundred?  The street was nearly filled with the bastards, from sidewalk to sidewalk, a mob between the Teeth and us.



They didn't seem to be smart enough to realize they could actually \emph{shoot }the guns, where the occasional Spree had one in hand, but the sound of a gunshot going off suggested that one had accidentally pulled a trigger.  The shot rang through the air, cutting through the thrum of raindrops striking ground.



Like the gunshot that marked the start of a race, it was the moment that brought the \emph{real} fighting to a peak.  The Teeth and our side all jumped into action.



My bugs flooded into the group, condensing on the key members.  I couldn't seem to touch the Spree that was generating the mindless clones, as his body vibrated and rippled, but I could attack Hemorrhagia, Animos, Butcher, Reaver, Vex and the underlings.  The press of near-identical bodies was almost \emph{useful, }giving my bugs shelter and dry surfaces to move on.



Codex advanced, breaking away from the rest of the Ambassadors.  She was a pale woman dressed in a white evening gown, wearing a simple, featureless white mask.  A temporary costume.



She reached towards the crowd.  I could see the eyes of the Sprees lighting up as the effect reached further back into the crowd.  They stumbled, slowing, blocking the ones behind them from advancing.  Groans and grunts echoed from the crowd, all eerily similar.



Their powers were new.  Less than six hours old.  Accord had agreed to lend them to us, though their costumes hadn't yet been designed, their powers not fully explored.  We'd offered Tattletale's analysis of their capabilities in exchange.  She'd barely been capable, hadn't yet recuperated from the migraines she'd suffered earlier in the week, and the use of her power had only brought the migraines back with a vengeance.



Still, we'd talked it over and agreed that the assistance of the Ambassadors as a whole was that much more useful in this scenario than a worn and weary Tattletale.  Tattletale's feedback was essential, but we already had a sense of who the Teeth were, and Tattletale had been able to fill \emph{us} in on the new Ambassadors just as readily as she'd filled Accord in.



Codex was a blaster-thinker hybrid.  Tattletale had speculated that the woman caused permanent brain damage and memory loss , briefly augmenting her own processing power in exchange.  The duplicates Spree was generating weren't gifted with much in the way of brains to begin with.  Even a little damage was having devastating results.



Jacklight was launching forth the miniscule orbs of light, each growing as it traveled before stopping in mid-air.  Each warped space around it, accelerated movement, enhanced the output of certain forms of energy.  Where one of his lights was set next to a wall, it redirected one running duplicate into a wall.  Another, closer to the ground, swung a Spree that stepped over it into the ground face first.



It was Ligeia, though, who slowed down the enemy the most.  She created water out of nothing, geysers of the stuff that drove the mob back and sent them sprawling.



Then she sucked up the water.  I wasn't entirely sure, but I got the impression she caught one or two duplicates in the process, drawing them into whatever place she'd taken the water from.



It took her a second each time she switched from creating water to drawing it in.  Clones slipped through the gaps in the defensive line as she changed gears.



``Rachel!'' I gave the order.  \emph{Before Jacklight's power makes it impossible to go further or more slip through}.



Her responding whistle cut through the night.  Bentley and three more dogs were released, charging forward, leaping over our defensive line to crash into a sea of duplicates.  The duplicates were now too closely packed together to even fall down, and were literally climbing over top of one another.  The dogs stumbled or slipped as the Jacklights tugged at one or two of their legs, then proceeded to tear their way through the crowd.



They were brought to a stop when they found the second of the Teeth's defensive powers waiting for them.  Vex's forcefields were countless, numbering in the hundreds, each sharp enough to cut exposed flesh.  Alone, they weren't strong, but the shards had a collective, cumulative resistance.  I'd hoped Rachel's dogs would have enough raw strength to power through.



Still, we had the advantage here.  The tide of the duplicates was slowed as the bludgeoning power of the dogs crumpled them underfoot or crushed them against one another, and both Barker and Biter were free to join the defensive line.  I was able to step back and get a brief respite from the hand to hand fighting with the Spree duplicates.



``Kip up!'' Rachel bellowed the words.



One dog leaped to the side, planting its feet on a wall, then leaped for the Teeth on the far side.



A four-legged creature just a little smaller than the dog lunged into the air, brought the two of them crashing down into the midst of the sea of tiny forcefields.  Animos.



Cape teams naturally found their own synergies and strategies.  This was how the Teeth fought.  Two defensive lines protecting the reserve forces while the truly dangerous members acted.



Butcher raised her gun, setting one finger on a trigger of her gun.  It started spinning up.



``Butcher incoming!'' I called out.



She teleported past the worst of Vex's forcefield barrier.  Flame billowed around her in a muted explosion as she appeared.



\emph{Butcher six's explosive teleporting.  It's weaker than it was when }\emph{six had it, shorter range, and the intensity of the explosion isn't nearly what it once was}.



She pushed past the remainder, and leveled the gatling gun at the nearest dog, pulled the trigger before anyone, Regent included, could do anything to trip her up.



Ten bullets were fired in a half-second.  A moment later, the weapon jammed.



Wounded but intact, the dog turned and snapped at her.



She was gone a heartbeat before the teeth snapped together.



\emph{Butcher three's danger sense.  Didn't do him much good.  Driven mad, died in a suicidal attack against the Teeth.  Window of opportunity is lower, application limited to more physical danger.}



She reappeared in a cloud of rolling flame, reversed her grip on her gatling gun and swung it like a club, knocking Bentley clean off his feet.



\emph{Super strength, courtesy of one, three, six, nine, eleven and thirteen.  Cumulative effects.  A little bit of super strength from multiple sources added up.}



Animos was pinned by another dog, a yellow light surrounding both of the unnatural beasts.  He screeched at the dog, a high-pitched noise that made me wince, but the effect didn't take hold.  Animos' scream could strip someone temporarily of their powers, but Citrine was dampening the effect.  That, or there was nothing to take away from the dog.  The mutation was \emph{Rachel's} power, technically.



Butcher approached the pair, and Citrine abandoned her assault, letting up.



As Tattletale had warned Grue, she'd warned Citrine as well. Butcher's power was too dangerous to muck with.  Grue risked absorbing the consciousness of the prior Butchers, and Citrine risked striking on the right `attunement' and accidentally killing Butcher.



But Citrine was still a leader, didn't waste a moment.  She gave the signal, shouted something I couldn't make out, and her followers opened fire.  Jacklight and Codex lobbed their attacks towards Butcher, and the leader of the Teeth teleported away before either could do any real damage.  Ligeia produced a geyser of water that sent duplicates flying ten or twelve feet in the air.  Othello, for his part, was standing by, his hands in his pockets, his two-tone mask expressionless.



Which wasn't to say he wasn't contributing.  Hemorrhagia was enduring an assault from an invisible, immaterial foe.  I could \emph{feel} him, feel the movement against my bugs, but the bugs didn't settle on him, simply passed through.  He was only partially there, focusing on allowing certain aspects of himself, his \emph{weapon}, to affect our world.



Shallow cuts appeared on Hemmorhagia's face, chest and arms as she tried ineffectually to shield herself, and those same cuts exploded violently as she used her power to draw her blood from her body and turn it into hard, physical, cutting weapons.  More blood congealed into broad scabs that protected her and reduced the damage of the continuous slashes.



A distance away, Imp appeared, electrocuting Spree with a jab of her taser and bringing an end to the stream of duplicates.  Not that the duplicates were doing as much damage as they had been.  Like lemmings running off a cliff, many were scaling the piles of fallen clones and promptly running into Vex's forcefields, only adding more corpses to the virtual hill of corpses that separated us from the other members of the Teeth.



Our two Strangers were doing much of the work in dealing with the back line.  That left us to deal with Butcher.



Bentley had recovered and charged her.  She responded by hitting him with a wave of pain, putting him off his guard so she could strike him aside.



\emph{Butcher one}.  \emph{Inflicted agony at range}.



Bentley was quick to recover, quick to push past the pain that she was inflicting and attack.  She prepared to strike him again.



Regent knocked her off-balance, and she was caught off guard as Bentley struck her with one paw.



She teleported out of Bentley's way before he could follow through with the attack, appeared in between Regent and I, surrounded by our capes.  We staggered back as flame washed over us.



I felt my focus begin to slip, thoughts of violence filling my mind.  I \emph{itched} to attack, to hurt her.



I sent my bugs in, but that was the one gesture that set the others in motion.  Without realizing it, I found myself charging her.



Biter and Regent were among those caught in her spell.  We attacked her as mindlessly as Spree duplicates had attacked us.



My knife stabbed at her armor, doing too little damage.  I stabbed again, found a vulnerable spot at the back of her neck, just below her hairline.  I dragged the knife through her flesh.



Without even turning to face me, she elbowed me, and all the strength I had went out of me.  I careened a distance away, tumbled, landed amidst Spree clones.



They clutched feebly at me while I reeled.



Lizardtail's power pressed even harder against me.  I could feel the edges of my injuries tingling, the wounds slowly knitting closed.  Far slower than they should have been, given the earlier demonstration of Lizardtail's power.  Either he was weaker, or her ability to inflict wounds that progressively got \emph{worse} over time was taking away from the power of his regeneration.



Butcher had a grip on Regent, threw him into Biter with enough strength to take the two of them out of the fight.



Possibly enough strength to kill one, if Lizardtail's power wasn't able to outpace the internal damage done.



\emph{Induces mindless rage.  Power from Butcher Nine.  Very low range.}



\emph{Inflicts wounds that fester.  Power from Butcher Four.  Less effect than Four had.  Far shorter duration.}



She teleported.  I could sense where she'd arrived as my bugs died en-masse.  She was going after Rachel.



I had lines of silk prepared, did what I could to bind Butcher.  She struggled briefly, then teleported free of them.



Codex and Ligeia directed attacks her way, and again, Butcher disappeared before either could really affect her.



I felt something shift inside me, and the pain dropped to a fraction of what it had been.  I got to my feet.



``Go!'' I shouted.  ``Get the wounded!''



Rachel whistled, and the dogs converged on our location.  Butcher had appeared in the midst of the Ambassadors, but the variety and ferocity of their attacks had her teleporting from moment to moment, doing more damage with the flames that appeared around her than through any action she could carry out.



It seemed that even though Codex's attack hadn't connected full force, Butcher wasn't keen on giving her an opportunity to deliver any more grazing hits.



Rachel stopped next to me, offered me a hand up.



``Fetch Codex,'' I said.  ``The Ambassador in white.  Butcher's going after her.  It might mean Codex is doing the most damage.''



Rachel gave me a curt nod, and we charged, leaving Grue to help Regent.



Butcher teleported away as Bentley hurtled at her.  I reached for Codex, took her hand.  She looked at Citrine, as if asking permission.



``Go,'' Citrine said.



I helped Codex up onto Bentley's back.  She had to sit sidesaddle.  Those ridiculous dresses.  They weren't meant for fighting.



But, then, I suspected that Accord was used to `shock and awe' tactics, when he had to engage in a direct assault.  How many of his enemies were as tough, versatile or persistent as Butcher?



She'd teleported away, effectively leaving her team to fend for themselves.  Only Reaver, Vex and, to a lesser degree, Hemorrhagia, were in fighting shape.  Butcher was interested only in the fight.  She was the central pillar of the Teeth, and stopping her would stop \emph{them}, and for much that reason, her team was a secondary concern to \emph{us} as well.



``Run!'' I told Rachel.  ``Codex, hit her where you can.''



I was versed in fighting teleporting foes, had engaged in a similar conflict against Oni Lee.  Butcher wasn't him.  She didn't obsessively use knives.



No, she was drawing a configuration of metal rods and panels from her back.  Her gun abandoned in the course of the fighting, she was unfolding the device into a different weapon.



A compound bow.



I already knew which power she was using next.  Imp had sabotaged the gun, jamming the ammo feed, but she hadn't been able to get at the bow.  It was massive when fully unfolded, nearly six feet long, not counting the extra length as part of the curve.  Large enough that it required superhuman strength to draw.



Less than a year ago, Butcher had been known as Quarrel, and as Tattletale told it, Quarrel had used a much smaller version of that same bow to kill Butcher Thirteen in a drawn-out fight in New York.



Regent wasn't in fighting shape.  My bugs weren't able to move fast enough to reach her.  Ligeia wasn't in a position to hit her with water, and Jacklight's orbs didn't reach nearly that far.



If she started shooting, we'd drop like flies.



``Hit her,'' I said.  ``Codex!''



Codex reached out to use her brain-drain attack.  It was visible only by the effects it had, but I'd seen it move through the Spree clones.  It was slow.



Butcher had time to string her bow before she had to teleport out of the way, appearing on top of a building with a vantage point of the battlefield.  She knelt, touching the rooftop, and reformed the stone into arrows.



That power was Butcher Eight's, except he'd had more reach, was faster.



Bugs clustered at her eyes, but she barely seemed to notice.  Nearly blind, she drew her string, pointed the arrow at us.



Before I could react, shout a warning, Codex hit me with enough force to nearly unseat me, despite how I was sitting astride Bentley.  Something else struck my shoulder with enough force to tear half the armor away.



The new villain slumped and fell, joined by the piece of my armor that had been shorn off.  An arrow neatly penetrated her neck.



Butcher drew her bow again.



She didn't miss.  She did something to warp space or adjust the very fabric of reality, so her shots always struck the intended target.



She aimed towards my teammates, paused, lowered her weapon a second as if momentarily confused.



The bow swept in the Ambassador's direction.



Then she turned, her body rotating, the massive bow and long arrow pointing at us.  Rachel and I.



``Go!'' I shouted.  ``Go, go!''



We could only get out of range.



How far could a bow like that send an arrow flying?



Apparently Butcher didn't think it would be \emph{this} far.  She teleported, paused, then teleported again.  A small fire erupted at each destination point.



Another teleport, and she killed a swarm of bugs I'd left lying in wait.  I'd hoped she would fall short, and that I could bind her weapon with silk.  No such luck.



``She's following!'' I shouted.



Rachel grunted a response, kicked Bentley to drive him to run faster, then whistled.



Her dogs broke away from the rest of the Ambassadors and Undersiders, trailing after us.  Butcher had to teleport as one spry, smaller dog noticed her and ascended to the rooftop to give chase.



Buying time, but she was closing the distance.



I drew from the silk I had stored in my utility compartment.  Coils of it, braided together into lines strong enough to suspend a grown man.



Hopefully strong enough to hold Butcher.



We had a plan, I just hadn't counted on her being quite as tenacious as she was.  I'd looked at the teleportation power, had failed to account for what it meant in conjunction with her danger sense.



I formed the silk into nets.  I could guess at her next destination, track her possible arrival points.



Again, she teleported right on top of a net.  The flames destroyed it.



One net left.



We'd reached the edge of the city.  There were fewer buildings, fewer rooftops.  Wet clumps of sand flew behind Bentley's feet as he dug deep to find traction.



Butcher appeared on one of the last remaining rooftops, killing a cloud of bugs.  Other ambient bugs clustered on her, biting and stinging, doing ineffectual damage. Too tough, courtesy of Butcher number\ldots fuck it.  Didn't matter, really.



She deemed herself close enough to take a shot, drew her arrow back, raising the bow so it pointed nearly at the sky.



The net closed around her, unseated her arrow from its mount.



Bugs wound more strands around her knees.  The wind pushed at her, and she tried to extend one foot to catch her balance, succeeded only in tipping herself over.  She fell from the roof of the five-story building.



She teleported herself right to the ground, cutting the height of her fall in half and freeing herself of the net.



It was still a hard landing.



``Get her!  Fetch her!''



Rachel nodded, whistled three times, pointed.



The dogs that trailed after us were quick to follow the order, snatching up Butcher.



She'd heal, was probably healing the brain damage Codex had inflicted.  Butcher was tough enough that the dogs probably wouldn't do enough damage before she regained her senses.



I might have been wrong in that assumption, but we couldn't afford to think otherwise.



``Go!''  I shouted.



We ran.  Rachel and I on Bentley, a pack of her dogs following behind.



There was no telling how much time we had.



We'd gone into this with one plan.  One solid way of putting an end to Butcher.  It was why we weren't hiding in the safety of Grue's darkness.



Though we were in less danger than we'd been since the battle started, my heart was pounding harder than ever.



``Stop!'' I called out, to be heard over the wind.



Rachel pulled Bentley to a stop.  She knew what came next, gave a hand signal.  ``Dogs, stop!  Rat-dog, forward!'



The dog that had Butcher ran on a little further, passing over a line of stones in the wet sand.



``Shake!''



Rat-dog shook Butcher like she was a chew toy.



``Good dog,'' Rachel said.  ``Drop her.''



Rat-dog dropped Butcher.



``Come.''



Rat-dog whimpered.



``Good boy, come.''



Tail between his legs, Rat-dog approached, passing over the line of stones in the wet sand.



Long seconds passed.  Bentley virtually \emph{heaved} with the exertion of the run.



My eyes didn't leave Butcher.



Butcher roused, and it wasn't a slow affair.  One instant she was lying prone, the next she'd teleported, appeared next to the narrow, light-bodied dog and bludgeoned it, sending it flying.



``Dakota, go!  Bear, go!''



Two more dogs charged Butcher, drove her back.



``Stop,'' I warned Rachel.  I lowered my voice, ``She has that rage aura.''



It didn't matter.  Butcher dispatched the two dogs just as easily, eyed us warily as Rachel commanded them to retreat.



``Good dogs,'' Rachel said, as they hurried to her side.



My eyes still didn't leave Butcher.  I watched, waited.



She didn't understand what was going on, why we weren't pressing the attack.



But she wasn't confident either.



She strung her bow, as if testing us.  She started to create an arrow out of sand, condensing it into a more solid form.



Then she gave up, stepped back.  The hardened rod of sand crumbled.



``Stop it,'' she said.



I shook my head.



She lashed out, hit us with raw pain.



In the agony, the feeling of fire running through my veins, I toppled from Bentley's back.



I'd anticipated this, or something like it, knew it was temporary.  I could only grit my teeth and tell myself it was almost the best case scenario, even when it didn't quite feel like it.



Rachel's dogs bristled, but the pain dissipated, and she found herself free to command them to stand down.



It didn't matter.  Butcher was on her knees now, face turned toward the ground.



``Don't say anything,'' I murmured.



With more focus than before, Butcher formed a spike out of hard sand.



She was murmuring to herself now.  Conversing under her breath with the voices in her head.  She sounded oddly insistent, plaintive in a very childish manner.



When the weapon was formed, she glanced skyward, murmured something indistinct.



Then teleported a distance into the air, directly above the spike.



There was a wet sound, a pause.



``Nothing?'' I asked Rachel.  ``You\ldots don't feel her powers?''



She shook her head.



``Then let's go.''



We began our long journey back to the others, leaving Butcher with a spike through her heart.



No rush.  The fight was over.  One more foe taken down.



If the PRT happened to wonder if any of the Undersiders or Ambassadors had acquired Butcher's powers, all the better.



``Mind if I come by tonight?'' I asked, my voice low.



Rachel shot me a glower over her shoulder, ``Why?''



``To talk.''



``We can talk now.''



``And so I can see how you're coping with your minions.''



``Whatever,'' she said.



``Is that a yes?''



``It's a whatever,'' she said.  ``Do whatever you want.''



``Okay,'' I said.



There was no more conversation as we closed the distance to the others.



They were more or less in ship-shape when we arrived.  Regent was propped up against a wall, but he wasn't pulverized.  The only one we'd lost was Codex.



``Success?'' Grue asked.



``Success,'' I said.



The entire group, even the straight-backed Ambassadors, seemed to react with relief.



``Guess my sister has one more kill under her belt,'' Regent commented.  ``Fourteen voices in Cherish's head to keep her company as she spends the next few centuries alone at the bottom of the bay.''



\blacksquare



``Daddy!'' a toddler squealed.  No older than three, the small child waded past a pack of dogs to her father, the tall, large-bellied man who I'd seen handling some of Rachel's dogs.



Rachel ignored the reunion, greeted the dogs who milled around her, barking and whining in joy as their master returned.



``Food?'' she asked me, almost as if it were an afterthought.



``Sure.''



``Someone make food,'' she declared.



``I will!'' a darker-skinned teenage girl declared.  She looked to be of mixed race, with brilliant blue eyes that didn't match up with her brown, coarse hair and skin.



``Hamburger,'' Rachel said.



``Okay,'' the kid said.  ``Anything else?''



``No.''



``Vegetables,'' I cut in.  ``Something healthier.''



Rachel shrugged.  ``That grilled crap you made before, with the\ldots long green vegetables.''



``The asparagus?''



``Yeah.  That was good.''



The kid looked like she'd just won the lottery, almost bursting with joy.



Barker, Biter and the veterinarian all set to basic chores around the place, as if it were routine.  No one seemed to begrudge the fact that Bitch was taking it easy while they worked, not even Barker, who had been somewhat prickly the last time I'd run across him.



Either she'd earned their respect, or they'd learned how stubborn she was.



``I wanted to talk to you about the future,'' I said.



``Mm,'' Rachel said, reclining.  The dogs were clustered around her feet, the larger ones laying their heads in her lap.



``It's\ldots problematic, having you patrolling the area out here, scaring the locals.  You know that, right?''



Rachel shrugged, apparently unconcerned.



I watched as the man with the three year old girl joined one of Bitch's other followers, a woman who had apparently been babysitting the child.  He fished in one pocket for money, then handed it over.



His voice was quiet, a mumble, ``When some'dy helps you out, what d'you say?''



``Thank you!'' the toddler chirped.



The woman only scowled.  I saw Rachel out of the corner of one eye, watching.



The man made his way past the kitchen, nearly running into the darker-skinned girl who was already cooking, past Barker and Biter, before finding a place to sit with his child.



Despite his size, his presence, the man with the child didn't make eye contact with anyone.  Almost flinched at it, even in the face of a hundred-pound girl.



Mentally disabled?  Developmentally delayed?  Or had he suffered a trauma?



Between the way the girl had been so overjoyed at the slightest praise, and this man's attitude, I was wondering if maybe Rachel's people were somehow just as damaged as she was.



``There's one possibility,'' I said to Rachel.  ``A role you could play in this.  You don't have to.  Just putting it out there.''



``What's that?''



``The portal, it sounds like it's going to be a thing.  There's a whole world out there with nobody around.  People will be settling there, establishing a society.  I'm imagining there'll be something of a society popping up around the portal, a mirror city to Brockton Bay.  But there'll be pioneers as well.  People striking out on their own.  And some of the Undersider's enemies are going to try to slip through, control things on the other side.''



``And?''



``If you're willing, maybe you could serve as an aide to the Undersiders, but you patrol for trouble, track down troublemakers and fugitives.  \emph{That} could be your territory, more than just the fringes of this city.''



She frowned.



``It's just an idea.''



``It'd be hard to feed my dogs.''



``Manageable,'' I said.  ``Tattletale aims to control one of the fleets that brings supplies to the other side.  We don't know how restrictive the government will be with the portal, or where ownership will lie, but\ldots I don't imagine getting dog food to you will be a problem.  And as the area gets settled, maybe you could supply trained dogs to pioneers or hunters looking to capitalize on the area.''



She didn't reply, focusing on her adoring dogs, instead.  Two hands, no less than twenty ears to scratch in her reach.



``Think about it,'' I said.



``Mm,'' she grunted.



The man was playing with his daughter, who was squealing and reaching out to pet the dogs who were standing by, almost protective.



``They're okay?'' I asked.  ``The dogs won't hurt the kid?''



``None of the dogs at this shelter,'' Rachel said.  ``Picked them carefully.''



I was a little stunned at that.  To give that much thought to something like that\ldots it wasn't in her character.



``Why?'' I asked.



``You said I should think about what people need from dogs.  If I'm going to find them homes, the dogs need to be able to live with families.''



I nodded.  There were more questions I wanted to ask, but I didn't want to spoil the quiet relief I felt at hearing her say that.



We sat for ten more minutes before Bitch rose and began playing with dogs.  She incorporated training into the play, dividing dogs into teams and having them fetch in shifts, among other things.  I stood, joining her, and she handed me a ball.



There wasn't much more conversation beyond that.  Most of the talking was reserved for the dogs.



Time passed quickly enough that I was surprised that Rachel's henchperson announced that the food was ready.  Not everyone collected some.  Barker and Biter held off.  The vet had her hands full.  Rachel loaded up a plate with two burgers and a pile of grilled vegetables.  I took about half the portions she did.



It wasn't very good, but the kid seemed so pleased with herself that I couldn't say anything to that effect.  Rachel didn't seem to care, nor did the big man and his daughter.



``Thank you,'' the toddler piped up, sing-song, when she was done eating the bits of crumbled up hamburger and bun.



Rachel, for her part, only stood to grab a soda.  She mussed up the cook's hair on the way back, as if she were petting a dog.



\ldotsNot quite a leadership style I might have suggested, but the kid looked happy.



I finished what I could, considered throwing the rest to the dogs, then decided it was best not to risk angering Rachel.



It was late at night, now, but I didn't return to my lair.  We tended to the dogs, grooming them, cleaning their ears and brushing their teeth.  Certain dogs were due pills, and Rachel saw to it that they got the pills.



It was an endless sequence of those little tasks I'd always found frustrating.  Cleaning up, doing jobs that would only be undone by the next day, if not within minutes.  I'd always found them frustrating, found it tolerable only now that I could delegate bugs to many of them.



Rachel reveled in it.  It seemed to calm her, center her.



The others found their way to their beds, or made their way out the front door to head back to wherever they lived.  Many dogs retreated to the kennels that were set out for each of them, and Rachel took the time to lock them in.



The night was creeping on, and I wasn't leaving.  I knew why, didn't want to admit it to myself.



Exhaustion overtook me eventually, though I would have been hard pressed to say exactly when.



I woke in the middle of the evening, found myself slumped on a couch with a crick in my neck, a blanket over me.



Rachel was on another couch, and the blue-eyed girl, the cook, was lying beside her, her back pressed to Rachel's front.



I stood, stretched, winced at the knot at the muscle where my neck met my shoulder.  The movement seemed to stir Rachel.  She started to extricate herself from behind the girl.



``Don't let me disturb you,'' I murmured, keeping my voice quiet enough that it wouldn't disturb anyone.



She shifted position, keeping herself propped up, ``You leaving?''



I frowned, ``Yeah.''



``Okay.''  She settled back down, and the kid curled up against her.  \emph{Kid}.  The teenager was probably older than Aisha or Vista.  I couldn't help but see her as younger, because there was something about her that screamed `lost'.



Maybe that was the role that Rachel filled, here.  Forming a screwed up, antisocial family with those who had nobody else.  Damaged people.



I was okay with that.  I could believe that, even if she didn't heal them or help them get better in any explicit way, she wouldn't make them worse.



I felt like I should say something more, but I was tired, my thoughts increasingly occupied by greater matters.  ``Bye.''



``Bye,'' she said.



I headed to the door.  I was already gathering bugs to me, just to ensure I had a safe walk back.  A walk home in the dark would be nice.  Time to think.



``Thanks.''



I stopped in my tracks, looked back.



Rachel had her head down against the armrest of the couch.  I couldn't see her through the other girl's head.



But it had been her voice.



I revised my opinion.  Maybe they \emph{could} heal each other, in their own ways.



It helped, as I stepped outside and started my long, quiet trek home.  I was riddled with doubts, with countless worries, but knowing that Rachel was in a better place was a light in the darkness.



I had let two days pass since my conversation with Miss Militia.  Dealt with the Teeth.  They weren't all gone.  Hemorrhagia had slipped away, as had Reaver, and there were rank and file troops.  Parian still had some cleaning up to do, at the very least, but the Teeth weren't the presence they had been.



Now I had to face everything I'd been dreading.  I'd spent time here because I was procrastinating.  Putting off the inevitable.  I couldn't put it off any longer: if I didn't bring myself to do it \emph{soon}, it would only get harder to bring myself to do it.



\emph{Tomorrow morning, }I thought.\emph{  I face off with Tagg and the rest of the PRT.}





