





I eased the door closed, then paused to let my eyes adjust.



Every window had the blinds closed and curtains shut over it.  The room was dusty, and needle-thin rays of light caught the flurries of specks, making them glow.



I grew aware of my surroundings, distinguishing dark gray shapes from an oppressive darkness.  A desk sat in the middle of the room, shaped like a `c', with a cushy computer chair in the middle.  Four monitors were arranged at even intervals across the desk.  Beyond them, three widescreen televisions were mounted on tripods.  The walls and open spaces beyond the televisions, in turn, were filled with bulletin boards and whiteboards.



I glanced at my phone.  The last text I'd received was still displayed on the main screen:



the nearest keyboard to entrance.  don' wander and don't turn monitor on.  type WQtksDH2.



I followed the instructions, making my way to the desk, carefully angling my body so I wouldn't touch any of the bulletin boards, and so that I didn't bump anything with the loose fabric of my running pants or my backpack.  I didn't want to risk using my bugs to check for obstacles, so I was forced to rely on my eyes alone, in this near-total darkness.



I found the keyboard, found the little nibs on the `f' and `j' keys so I could center my hand, and very carefully typed out the password.



A series of barely-audible `beeps' sounded throughout the room.  What had I just disabled?  Claymores?



Did I really want to know?



Free of whatever safeguards that had been set in place, I turned on the monitor.  The faint glow lit up one half of the room, casting light on Tattletale's costume in one corner, and the heavy metal door leading to her bedroom.



I found a dimmer switch on the wall and turned the lights up just enough that I could see.  The details on the bulletin boards became clear.  They were color coded by subject, but there were threads connecting elements, pieces of yarn tacked into place or held in spots with magnets.



I approached the nearest boards.  The set furthest to the left were each headed `Cauldron', with subheadings, and had either green construction paper or words in green marker.  The board closest to me had photos of various capes, organized into forty rows and twenty-five columns, headed `Cauldron, unconfirmed'.  One-and-a-half inch by one inch images of various masks, their names penned in underneath.  Here and there, portraits were missing, presumably where Tattletale had found better spots for them.



So many capes.  It was startling really, and I was suspicious it was incomplete.  Was she planning on expanding that?



The upper half had sections marked for `likely' and `confirmed'.  Many of the `likely' capes had a series of letters and numbers by their name, five digits long: reference numbers.



There were only three `confirmed' capes on the board.  Capes that had been more or less verified, through a combination of admission and Tattletale's powers:  Eidolon, Alexandria, Legend.



Lines were drawn on the construction paper behind them, pointing to one portrait-sized rectangle of paper at the top, as though indicating a hierarchy.  It was blank, and the `name' at the very bottom was only `Cauldron?'.



The back of the same bulletin board had `confirmed trigger' capes and `Case 53'.  Each `trigger' cape had a trigger event marked in pen below the name, along with the same series of letters and numbers by their name:  Jadeite: Post-brainwashing dissonance HSPuT.  Gethsemane: Lost family in war H2UXa.  Skitter: Bullying 9Zw3t.



The rest of the Undersiders were on that section of the board as well, but the trigger events had been left off.  Chances were good that she didn't want prying eyes to dig up details, while my information was presumably public knowledge.



I walked across her setup, my hand trailing across the index cards and pictures as I walked, as though I could take in the information through touch.



Lengths of yarn connected the `Cauldron' board to the PRT board, which was a whiteboard, magnets affixing index cards to specific areas.  A black piece of yarn extended from Alexandria on the `Cauldron' board to the recently retired Chief Director on the `PRT' board.  Black for a direct connection?  Yellow yarn extended from the Cauldron board to index cards regarding PRT funds.



The whiteboard held scrawlings of notes, musings and possibilities, some half-erased.  \emph{Degree of involvement with Cauldron}?  \emph{Funding: is PRT siphoning official funds to pay for powers?  Agenda?}



It wasn't reassuring.  The number of questions, the idea that the PRT might be far larger than I'd conceived.



I moved on to boards of a different color.  The red bulletin boards and whiteboards with red writing: Brockton Bay.  \emph{Potential threats: the Teeth, Red Handed, Heartbreaker, Lost Garden, Adepts, the Orchard, The Fallen.}



Each was labeled with a code, much like the trigger events had been, and a letter-number combination after that.



It took me only a minute to find what they were referring to.  Things were organized beyond the initial veneer of chaos.  A small bookshelf, knee-high, held file folders with the same letter-number pairings as I saw on the bulletin board.  I picked one out at random.



Adepts.  Self professed magic users.  One page of information, listing names and powers.  Another page with the PRT's information on them: a series of codes and symbols I didn't quite follow, numbers inside colored circles, squares and diamonds.  From what I could gather, they had a low threat level, moderate crime rate, moderate `engagement' level, low activity level.  Led by Epoch, a time traveler.



Fun.  I didn't even want to think about the headaches that power would cause.



I put the folder away carefully, picked out another.  Lost Garden. High threat level, low crime rate, low engagement level and moderate activity level.  Leader, Barrow.  A powerful shaker, similar to Labyrinth, only rather more single-minded in what he did.  He couldn't leave the altered area he created around him, only extending it slowly to an area while letting it fade behind him, an effect described as `a depression' with overgrowth extending into the surrounding neighborhood.  Tattletale's own notes in the file suggested he was making slow but steady progress towards Brockton Bay, and that he had been since the portal appeared.



I flipped through the rest of the file.  What kind of people gravitated towards someone like that?  Apparently a lot of very young parahumans, boys and girls around Aisha's age, had gathered around the middle-aged Barrow.  A little creepy, when I imagined that collection of capes and the resulting dynamic.



I put the folder away, returned to the boards.  Brockton Bay had several more.  Money.  Planning.  Property acquisition priorities.  Property sales.  A whiteboard with the word `door' written in red, circled and underlined several times, surrounded by question marks.



Who would own the portal?



A single blue-lettered whiteboard with pale blue index cards.  At the very top was the title, in bold black letters:  Powers: Source.



I looked at the index cards that were fixed onto the board with magnets.  There were no real answers there.  Only questions and theorizing.  It was Tattletale's stream of consciousness distilled.



the whole?  pieces of greater puzzle but don't know what shape it takes.  place person thing or something less concrete?  what \underline{are} powers?  Mirror/extrapolation a consideration? is there link between there and here?



\underline{why}?  power distribution aimless simple chaotic.  mistake?  something go wrong?  is this only part of something greater?  scheme or something more base?



why trigger events?  why go to trouble?  Connection to the source?  tied to something primal or some scheme?  simple or complicated?



what is deviation between cauldron and typical trigger?  was there leak to water supply from cauldron?  Parasite?  look into epidemiology.  prob not.  get someone's story about process for getting powers from Cauldron for hints.



%%% <p style="padding-left:30px;">Who has answers?  if not thinkers then capes with closer connection to passenger?  PRT?  Cauldron?  S9?  other gov’ts?  what channels can I use to get these answers?  theft, coercion money goodwill barter?  have to set a value for an answer before raising idea with <del>coil</del> Skitter</p>



I frowned and stepped away.



The last board, far right, was backed by black construction paper.  At the top, printed on white index cards in bold black letters: `End of the World'.



The board was disturbingly empty.  Jack's picture was in the upper left corner with pieces of paper arranged below it, tracking everything that he'd done since he left the city.  Each piece of paper had names of known entities he'd interacted with in any direct fashion.  Sites the Nine had attacked, a string of small towns as they progressed in a zig-zagging fashion away from Brockton Bay.



Capes recruited to the group, capes slain.



The other three-quarters of that board were almost entirely clear, but for one index card in the upper-right:



limits to Dinah ability: can't see accurately points of interaction with power immune capes, precogs, situ change Thinkers. Limited sight past points of interaction.  these are `stoppers'



%%% <p style="padding-left:30px;">Hartford: No known stoppers in area.<br/>
Enfield: No known stoppers in area.<br/>
Chicopee: No known stoppers in area.<br/>
Southbridge: No known stoppers in area.<br/>
Boston, Charlestown Area:  Yes stoppers, no direct interaction b/w any stoppers and Nine.  <del>call to dble check with Still</del>.  no interaction<br/>
Toybox: No known stoppers.</p>



It made a lot of sense.  Tracking Jack's trail of destruction from the point he'd left the city, finding the point where Dinah couldn't or \emph{shouldn't} be able to see, using them to narrow down possibilities.



But the expanse of black on that board was daunting, considering everything that was at stake.



I made my way to the desk, set my backpack down on the ground, and took a seat in Tattletale's chair.  I pressed the power buttons for each of the other monitors, and they flickered on.  Checking the drawers, I found a remote, and turned each television on in turn.



Two televisions dedicated to news, one to business, each on mute, with captions spelling out the words as the reporters spoke.



The password I'd entered had apparently logged me into the computers as a guest.  I kicked off my shoes and set my feet on the desk, as I'd seen Tattletale do, slipping into her shoes for a moment.



Everything was arranged so it was in clear view: monitors, televisions, bulletin boards.  Looking at the notes, the different colors, the disorder and the number of questions, it made me think of a kind of paranoid schizophrenia, seeing connections everywhere.  Except she was \emph{right}.



Even logged in as a guest, I could see vestiges of the programs she'd installed on her main accounts: a stock ticker, a news ticker, weather, time, trending topics, social media feeds, several alert boxes for when pages relating to certain topics were updated or created.  Even the \emph{background} was a series of four video feeds from cameras that overlooked Brockton Bay.



That was just what was worked into the desktop, with no windows opened.



The monitors flickered with new information at a speed that was two or three times that of the televisions, and the material on the televisions wasn't exactly slow-paced.  The bulletin boards, conversely were static.  It was like a physical representation of what was going on in Tattletale's mind.  Information streaming in, details from other sources intruding as I tried to focus on only one.  And always, there were the questions in the background, the same ones marked on the bulletin board.  Things to keep in mind while she took in other details, constantly seeking out the connections that tied things together.  Did she simply sit here, taking it all in, while using her phone and the computer to manage the Undersider's business?



No small wonder she had overloaded on her power.



I opened up a browser window on the computer, logged into Parahumans Online.



Two new tabs.  A search for Skitter, a search for Taylor Hebert.



`About 95,000 posts relating to Skitter.'



`About 5,200 posts relating to Taylor Hebert.'



I sighed, closed the tabs, and then investigated the board for Brockton Bay.  It wasn't anything I wanted to read.



I had checked most of the pages up to the halfway point on page two of the Brockton Bay sub-board when the heavy metal door clicked and opened.  Tattletale- Lisa stepped out, wearing an oversized t-shirt and pyjama pants.  My momentary confusion on how to define her was due to the fact that her hair was down, which I associated with Tattletale, while she was in civilian clothes, which was naturally fit for the name `Lisa'.



``Su- oh hell,'' she broke off, recoiling in pain in the face of the dim lights and the glow of the various screens and monitors, shielding her eyes.



I hurried to reach for the dimmer switch, but she was already calling out a command, ``System, lights off.''



The lights went out.



``System, screens off.''



The televisions and computer monitors went dark.



``Sorry,'' I said, keeping my voice low.  ``Thought you'd have recovered more.''



``Nah,'' she said.  She still wasn't opening her eyes, and was speaking with a care that suggested even the sound of her own voice hurt her.  I could see dark circles under her eyes.  She probably hadn't slept recently.  ``But no big.''



``You could go back to bed,'' I said.



``No way am I missing this,'' she said.  ``My chair.''



I climbed out of the chair and turned it around so the seat was available to her.  She made her way there as if she were an old woman, eased herself into the seat and reclined, putting her feet on the desk.  One arm draped over her face so her eyes were hidden in the crook of her elbow.



``This setup\ldots all of this is too much for you,'' I said.  ``You're trying to handle too much at once.''



``Ironic,'' she mumbled, ``Coming from you.''



I took a seat on the edge of the desk.  ``You're bombarding yourself.  You should try to tackle one thing at a time.''



``Can't.  I focus on one thing, I let others fall by the wayside.  Too many bases to cover.''



``Maybe you \emph{should }let things fall by the wayside,'' I commented.  ``Is it so important to understand where powers come from?  Isn't it enough to run the city, watch out for enemies, and maybe devote weekends to figuring out this business with Jack?''



She groaned.



``Sorry,'' I said.  I was only giving her more cues and prompting involuntary uses of her power, making the problem worse.  Asking questions was cruel, with her like this.



``No.  No, it's okay.  It's \emph{all} related.  I described my power as being like a massive, three-dimensional game of Sudoku, right?  Spaces get filled in.''



``Yeah.''



``This\ldots if I get stuck somewhere, maybe there's something on the periphery that helps me figure it out from another angle.  If I'm going to tackle the problem, I gotta tackle the \emph{whole} problem.  Helps keep the facts straight.  Notice sooner when the wrong piece of information's in a spot.''



``You forgot to note that Accord buys powers,'' I said.  ``Came up a little while ago, didn't see them on the back of the green board.''



She put her feet down on the ground, as if she was going to spring up and make the necessary adjustment, then seemed to think twice about it.  She rested her elbows on the table and buried her face in her hands.



``I'll do it,'' I said.



``Index cards are on the shelf by the door.''



I got up and walked over to the shelf, fished around until I found the green index cards and a black felt-tip pen.  I wrote down, `Reminder: Accord buys powers from Cauldron to empower qualified underlings.  They don't know much about process, but he will.'



I pinned it up in the `Likely' section.



When I was done, I glanced back at Lisa, still resting her head in her hands.



I let a minute or two pass in silence, while she got her bearings.



``So,'' she finally said.



``So.''



``Sorry I took so long to show,'' she said.



``Not a problem,'' I said.  ``I enjoyed the peace.  A moment of quiet before the storm.''



``I'm not messing up your schedule?  What time is it?  Eight?''



I started to shake my head, then realized she wasn't looking at me.  Hard to tell in the gloom.  ``You aren't.  And it's about seven forty-five.''



``Not sure I follow this plan of yours.  That's a bad sign, if I can't get my head around it.''



``You're not exactly in the best shape.''



``Still.''



``Still,'' I echoed her, sighing.  I leaned against the wall, hooking my thumbs in my pockets.  ``Maybe you're right.''



She slowly raised her head, grimaced, and then shifted back to a reclining position, moving at a glacial speed.  I felt a pang of sympathy.



``Can I get you anything?''  I asked.



``Drugs don't help.''



``Something besides drugs, maybe.  Water.''



``No.  Nothing makes a difference except time, being very still, very dark and very quiet.  Let's just\ldots''



She trailed off.



``Let's just what?'' I prompted.



``I was going to say we should get this over with, but\ldots we don't want that, do we?''



``No,'' I said, my voice barely above a whisper.



Silence lingered.



I stared at the room, all the unanswered questions now illegible in the darkness, reduced to shades of dark gray on black, and black on dark gray.



Those questions were Lisa's province.  My focus was on the team, the dynamics of the group, and the how we handled those beyond our inner circle.  Our enemies, allies who could become enemies.  Even the public at large had to be handled, managed, addressed as a possible threat.



Those were the concerns I had right now.



``Wish I could use my power more,'' Lisa said, ``Give you advice so you're going in with your eyes wide open.''



``I wish you could too.  Don't be upset with yourself, though.  I didn't give you much advance warning, and you'd already overloaded your power.  The sentiment's enough.''



``It's not, really.  Fuck me.  I'm not very good at this.  Being uncertain.  Frustrated.  Disappointed in my inability to offer anything\ldots''



She trailed off.



I thought of the Lisa I knew, her personality, her general demeanor.  Slightly reckless, confident, cocky.  Fearless.



``And scared?'' I offered.



``Scared,'' she agreed.



I'd never really seen her vulnerable.  I'd seen her \emph{hurt}, had seen her reactions after her arm had been dislocated, after Jack had slashed her face open.  I'd seen her \emph{worried, }even \emph{spooked}, when the Endbringer was en-route, and when she'd been concerned for \emph{me}.



But this was \emph{Lisa, }temporarily bereft of her powers.  A mere mortal.



I wasn't sure how to respond to that.



``You know, Rachel said thank you last night,'' I said.



``Yeah?''



``Got me thinking,'' I said.  ``Don't know if I ever said it to you.  I owe you the most, in a way.''



Lisa smiled, but it wasn't a joyful expression.  She murmured, ``Don't know if you should be that thankful.  What I did, bringing you on board, trying to help you, if I can even call it help, considering where we wound up.''



``The means justify the end, maybe,'' I suggested.



``Maybe.''



``I appreciate it, whatever the case,'' I told her.



``Then you're welcome,'' she said.



She changed position, and I made out a nearly imperceptible noise of pain.



``And I think that's my cue to go,'' I told her.



She frowned, ``Damn.  That's it?''



I shrugged.  ``What more is there to say?''



``I'm supposed to give you advice.  Some insight.  But I'm crapped out.''



``Give it a shot anyways,'' I suggested.



She frowned.  After a few seconds, she said, ``Give 'em hell.''



``Will do,'' I said.  I approached her, then leaned down and wrapped my arms around her, while she was still sitting in the chair.  One gesture, as if it could convey everything I couldn't say with words.



Grue had worried I was fatalistic.  That wasn't quite the term that applied, here.  But the underlying idea was sound.



We'd established something of a rule, way back when, on the night we'd first found out about Dinah and her powers, the same night Leviathan had arrived.  I'd very nearly turned my back on the group, and Tattletale had established a rule.



No goodbyes.



I collected my backpack, turned, and then left, wordless.



The sun and the heat were working on destroying the fog that had settled around the city in the wake of the grim weather.  The result was that the sky was very blue overhead, the city still harboring traces of the early morning's fog.  It couldn't be later than nine.



I wasn't wearing a costume, but I wasn't hiding in clothing I wouldn't normally wear, either.  A simple white tank top, black running pants and running shoes.  For all the bystanders could see, I was Taylor Hebert, indistinguishable in appearance or fashion from the girl who'd appeared on the news.



Nobody gave me a second glance.  I moved with purpose, and that was enough.  The eyes in the crowd looked right past me.



It had taken me some time to get used to the sheer \emph{obliviousness} of people.  Even Rachel, with her distinct appearance, had been able to manage with brief public appearances.  It was less about \emph{getting caught}, more about escape routes.  Being spotted while I was on my way to visit Grue and Citrine would have been problematic.  Being spotted on my way back to my territory wasn't a problem.  By the time the heroes could respond, they wouldn't be cause for any concern.



The same principle applied here.  The only distinction was \emph{why} the heroes weren't a cause for concern.



Tension sang through my body with every step.  My stomach felt hollow – I hadn't had much of an appetite this morning.



At the same time, I felt an almost zen calm.  My thoughts were clear.  I'd already decided on a plan of action.  It was a similar calm to the one I'd experienced against Dragon and Defiant.



I approached the PRT headquarters.  Many of the bugs I'd infested the building with on my last visit were still there, and the occupants of the building had adjusted to them.  Nobody gave a second thought to the bugs that made contact with them, unless it was to absently slap at a mosquito or brush an ant from their leg.



I could sense Tagg in his office, talking on the phone.



People were filing in through the front doors, some were employees, others were tourists, eager to check out the newly opened gift shop and inquire about a tour.  It was puzzling.  Did Tagg not anticipate another attack?  Or had he decided that my attack with my bugs was the very extreme to which I was ready to go?  The full extent of the threat I posed when angered?



The PRT officers stationed just inside the door, grown men and women who had the \emph{job} of looking out for troublemakers, barely glanced at me as I joined the crowd and walked right under their noses.



Then again, I'd said something to Regent about that.  Attacking from an unexpected direction, doing the last thing one's enemy expected.  This was definitely that.  There was no way they expected me to walk into the building, first thing in the morning on a sunny day, when they hadn't even done anything in recent memory to provoke me.



I made my way into the center of the lobby and stopped to looked around.



Maybe it was that I was standing still, while the rest of the people in the lobby were moving.  If not moving against the flow, resisting it.  But someone noticed me.  A PRT officer by the front desk.  I could see him out of the corner of my eye, reaching for his weapon.



I exhaled slowly.  I felt eerily calm, while my power roared at the periphery of my consciousness.  It was as if my bugs were screaming at me to attack, to retaliate.  To strip flesh from bone, sting and bite.



I pushed my bugs back, told them to go still.  It had been months since my power and I were this at odds.  Months since I'd been in the bathroom of Winslow High, telling myself\emph{ } I \emph{didn't} want to fight, that I didn't want to retaliate against the bullies.



But now I was left to wonder if that was my subconscious or my passenger?



``Villain!'' the PRT officer bellowed as he trained his gun on me.



The reaction was oddly delayed, as each one of the fifty or sixty people in the lobby turned to the PRT officer for a cue, for some indication of the danger or the direction of the threat.  They saw the direction that he was facing and the direction his gun was pointing, and turned their attention to me.



Only then did the civilians and unarmed staff scream, run, and seek cover.  Only then did the PRT officers around me draw weapons and point them at me.  A half-dozen PRT officers in full body armor, with their lethal and nonlethal weapons trained on me.



``Get down!'' one officer screamed.



I slowly dropped to my knees, then folded my hands behind my head.



There were sounds of footsteps.  I could see Miss Militia and the Wards exiting a room behind the front desk.  I tried to think of what my bugs had told me about the layout on past visits.  It was a meeting room, if I was remembering right.



Miss Militia, Clockblocker, Flechette, Vista, and Crucible stared, eyes wide.  Miss Militia's expression was one of concern, her eyebrows furrowed.  She was still, compared to the PRT officers around me, who were shouting at me, asking questions I couldn't answer.  I bowed my head and closed my eyes, as if I could find the same kind of refuge Tattletale had been seeking, find a stillness by shutting out the chaos of the outside world.



I'd said my goodbyes to my team, as much as I'd been able.



I'd put my ducks in a row, again, as much as I could.  I'd have to trust to Grue to see to Regent and Aisha, keep them on the right path.  I'd have to trust Tattletale to look after Grue.



I'd decided, in the course of talking to my mom, that I'd have to cross a line if I was going to follow Dinah's instructions, if I was going to achieve everything I needed and wanted to achieve.  To do it, I'd told her, I'd have to be heartless, and this was the most heartless, inhuman thing I could do.  Leaving my people.  Leaving Rachel.  Leaving Brian.



I thought of the paper, of the words from Dinah.  `Cut ties'.  \emph{I hope you know what you're doing, Dinah}. \emph{because this is as cut as I can get them.}



My eyes met Miss Militia's.



``I surrender.''





