





The Number Man swept one finger over the touchscreen display.  Two point six billion dollars here, a hundred thousand dollars there.



Money was the blood of civilized society, its currents running through everything and everyone.  Where money was insufficient, things withered.  People starved, sickened and died, constructions eroded, even ideas perished.  Where funds were plentiful, the same things blossomed with new life.



And money was, in the end, little more than the product of collective imagination.  A slip of paper or a coin had no value beyond that of the material it was fashioned of.  It only took on a life of its own when people as a whole collectively agreed that certain papers and coins were worth something.



Only then did people bleed and die for it.  For a fantasy, a faith given form in hard, concrete numbers.



Then again, much of society was built on a series of shared delusions.  Clothing was little more than scraps of particular materials with particular geometries, but people clung to the idea of \emph{fashion.  }Style.  Good and bad fashion was another belief system, one which all members of a culture were indoctrinated into.  Breaking certain conventions didn't only challenge the aesthetic sensibilities of others, but it challenged their sense of \emph{self.  }It reminded them, subconsciously, of the very \emph{pretendings} they clung to.



Only those with power could stand against society's tides, flaunt the collective's `safe' aesthetic.  When one had enough power, others couldn't rise against them and safely say something calculated to reduce their own dissonance and remind the offending party of the unspoken rules.



When one had enough power to take a life with a twitch of a finger, a \emph{thought}, they earned the right to wear skin-tight clothing and call themselves Hero, or Legend.  To wear a mask and name themselves something inane like `the Cockatoo' and still take themselves seriously.



He armored himself in normalcy.  He wore only a button-up shirt and thin-rimmed glasses, his blond hair cut into a short style that was easy to maintain.  To anyone on the street, he wouldn't appear to be anything but a bookish middle-aged man.



He hadn't always been this bland.



The Number Man stepped away from the screen.  His office was plain, white tile with white walls. The rear of it was a floor-to-ceiling window, looking out on a foreign landscape, a place far from Earth.  Still \emph{an} Earth, but not the one he'd been born to, not even the one he was in at this very moment.  The Doormaker maintained a portal to that foreign landscape, just behind the Number Man's office and changed it on request.  Today, it was a mountaintop view of a wilderness with a crimson foliage and gray branches, the sky perpetually overcast.



One of a number of Earths where humans had never been.



The Number Man had gone to some lengths to spruce up this place.  He'd never liked the eternal white of this complex, so he'd adorned his walls with other images.  To his right, there was a large print of the Golden Mean, the Phi decimal as a fractal image in gold against black paper, with mathematical notation surrounding it.



Opposite it, Dali's Crucifixion, \emph{Corpus Hypercubus.  }The painting was blown up to one-and-a-half times the size.  Jesus crucified on a fourth dimensional cross.



No chairs.  He'd worked out the dangers of sitting against the convenience and decided it wasn't worth falling into that trap.  When he did enter his office, he walked, paced, tapped his foot while pondering deeper problems, stood and stared out the window at whatever landscape he had outside his window in a given week.



He crossed his room and touched a screen.  It lit up, filled with data fed to his computers from a doorway to Earth Bet.  The pulse of society, right under his thumb.



The Elite, a villain group expanding a subtle control over the western seaboard of America, putting pressure on rogues to bring them under their thumb as performers, thinkers, designers and innovators.  He could see the numbers, extrapolate from the data to gauge their rate of growth.  They were developing too slowly to be useful, not developing fast enough to outpace the predicted end of the world.  They'd reach Brockton Bay in about a year.  There would be time to decide if countermeasures were needed in the meantime.



Gesellschaft, a nationalistic organization half a planet away from the Elite, was moving large funds in anticipation of a small war.  Money was being laundered through cover operations and businesses, almost impossible to track, unless one was able to take in the bigger picture, to see the \emph{intent}, the beginnings and endings of it.  They were investing in transportation, and their fundings seemed to decline at the same time some notable arms dealers in Southern Europe found themselves richer by an equal amount.  The Number Man flicked his way past a series of windows detailing the transaction amounts.  Arms dealers who specialized in nuclear materials.  This was pointing towards terrorism, and not on a small scale.  Troubling, but the system would address them.  The major hero group in Germany, the Meisters, would attend to the problem.  It didn't warrant an expenditure of Cauldron's full resources, not when things were already on shaky ground.



Still, it wouldn't do to have a disaster at this crucial juncture.  The Protectorate was required for just a little longer.  If they were going to make it through this, there couldn't be any substantial distractions.



Gesellschaft hadn't elected to seek out the Number Man and make use of his services, as so many supervillains around the world did.  He had no compunctions, as a consequence, about interfering with them.  He tapped into a series of bank accounts he hadn't touched in some time, then scheduled a large number of transfers to the personal Gesellschaft accounts.  Ten or twenty thousand Euros at a time.



Where funds weren't likely to be held for moderation, he scheduled more transfers and disputed the charges.  The transfer amounts were large enough to raise flags, to draw attention to the accounts in question.  The banks were on the lookout for suspicious activity, and a total of five hundred thousand Euros appearing in six checking accounts with typical balances of under a thousand Euros would be suspicious enough to merit a serious look.



That was only to slow them down.  They would want to investigate, to be careful and find out where the money came from.  Later, if the situation was resolved and they somehow managed to hold on to the money, they would want to know where the money disappeared to, as he reclaimed it with a severe interest rate.  They would suspect interference, would wonder if this outside agent had connected their civilian identities to their personas within Gesellschaft.



Which he had.



The transfers took him less than thirty seconds to arrange, and it would occupy them for one or two days.



Freezing the larger business accounts would take only a little more time.  One or two minutes.  The meetings with the arms dealers had fit a vague schedule.  The arms dealers always took a different route, but they traveled enough that they needed to buy gas at one point on the way.  There was always a large transfer of funds.



He laid a trap, calculated to start falling into place when the gas was bought in the time window.  The main accounts that the Gesellschaft used to manage their funds would be frozen by the time the meeting was underway.  They'd likely find themselves at the meeting, the product delivered, but with no funds to pay for it.



He swept his fingertips along the window, dismissing the task.  Who else?  Where were the priorities?



The C.U.I. had bought a parahuman.  Not so unusual.  Higher rates, as of late, but then, the C.U.I. faced a slight chance of an Endbringer attack in coming weeks.  They would want to bolster their forces, add parahumans to their peculiar team.



Tattletale had been actively separating herself from the Number Man, issuing new accounts to the Undersiders and her organization.  Not so surprising.  Eidolon had outed him, announcing the Number Man as a Cauldron-involved cape to a crowd.



Irritating.  At least it had been manageable.  He didn't exactly have a great deal of traction with the hero community.  Tattletale was one loss, and he was hands-off with the Undersiders, regardless.



The King's Men were in debt.  Easy enough to manage an anonymous donation, keep them afloat for another two months.



Child's play, all of it.  The money, with its imaginary value, it was something he \emph{breathed}.  Setting up the tools to manipulate it had taken a little time, but that was it.  Numbers were the fundament of the universe, as much a fabrication as money in some ways, more real than anything else in others.



He understood numbers, and through them, he understood \emph{everything}.



A soft beep marked the arrival of somebody at his door.  He turned.  ``Enter.''



There was only one person it could logically be.  The Doctor only sent her personal bodyguard and right-hand woman to him, the others didn't have access to this building.



Except it wasn't a person.  The door swung open, but there was nobody on the other side.



``You can't handle it yourself?'' he asked.



No reply, of course.



He broke into a quick stride, hurrying through the door.  ``Contessa is busy, I take it?''



Again, no reply.



He reached an intersection and felt his hair stir imperceptibly, little more than what one might excuse as the exhaust from an air conditioning vent thirty feet away.  He took that as his cue to change direction.



He knew where he was going, now.  He was relieved that it wasn't the worst case scenario, if one could call it that.  A mercenary calling herself Faultline had been leading a team that was opening portals for exorbitant amounts, traveling the world.  It was a matter of time before someone contacted her to ask her to open a portal to \emph{here}, or her own curiosity about Cauldron happened to lead her down that same road.



If and when that happened, the young woman and her team\ldots perhaps \emph{organization }was more fitting now that their numbers had grown, would get a visit from Contessa.  They would be removed from consideration, the portal would be sealed, and Cauldron would be safe again.



In the meantime, they'd let things carry on like they were.  Faultline would make contacts, she'd find like-minded individuals, and through her, Cauldron would uncover enemies, to be eliminated in one fell swoop.



At the very least, right here and right now, the threat wasn't an \emph{invader}.  Given the layout of the complex, and the fact that whole wings of the structure were on separate continents, linked only by the Doormaker, there were only a few possibilities for why an invader would be \emph{here}.  Not that it really mattered, it would be near impossible for someone to find their way here, \emph{now.}



No, this was a threat from within.



Double doors unlocked and slid open.  The Number Man wrinkled his nose as he entered the basement areas of the building.



When the Simurgh had attacked Madison, she'd copied Haywire's technology to open a gate to a building much like this one.  A research facility.  The portal had dumped the buildings, soil, plant life and all the residents into the city on Earth Bet, costing Cauldron a horrific amount.  Even a stockpile of formulae had been lost.



Perhaps most frustrating was the knowledge, the near \emph{certainty}, that they'd been near a breakthrough.  She'd sensed, somehow, had known, and had dashed it to pieces with the ease that a person might tear down a painstakingly made sandcastle.



They'd rebuilt, and this facility was somewhat different.  More reinforced, connected to the surrounding terrain.



Silly, to think she'd do the same thing twice, but they'd felt it necessary, after feeling the losses of that last attack.



The architecture here wasn't white, and he was somewhat relieved at that.  The tile was dark gray, lit by fluorescent bulbs and the light from windows at the end of the hallway.  At regular intervals down the hallway, there were cells.  Only some had windows to keep the occupants within.  Others had only three walls and a white line that marked the division between the cell and the hallway.



In each cell was an occupant.  Large metal plates engraved with numbers helped track who they were, matched to the numbers hidden in the right `arm' of the tattoo that each subject received; a series of white dots that looked like nothing more than areas where the tattoo hadn't taken.



The cells on the right were new test subjects, lost and angry.  He didn't hesitate as he walked past them.  The angry words they spat in alien languages were nothing to him.  Their glares and hatred less than that.



Their powers were only a small consideration.  It was a rare parahuman that didn't try to move beyond the boundary of their cell.  There was no forcefield to stop them.  They inevitably ignored the warnings and gestures from those in neighboring cells, stepping free, or they used their power, teleporting free or lashing out at one of the staff.  The Doctor, the Number Man, Contessa.



They learned after the first time.



Several staff members were housed in the cells to the Number Man's left.  Those cells didn't open directly into the hallway.  There were short paths that led around to the back of the room.  It helped mask the noise, gave them some privacy.  The cells were bigger too.



Zero-twenty-three, with a placard beneath.  `Doormaker'.



Two-six-five.  No name.  The Number Man knew him well enough, regardless.  He'd been too young a subject when he'd taken the formula, his brain too malleable for the required changes, too slow to form natural immunities and defenses.  Not a problem with regular trigger events, as it was.  The boy's eyes had burned out of his sockets as he'd tried to process the vast amount of information he was capable of perceiving.  Even now as he was reaching his late teens, the boy's mind had never developed beyond the mental age of eight, and his eyes remained like twin ashtrays.



A partner to the Doormaker, capable of granting clairvoyance, seeing whole other worlds at once.  It left most subjects incapacitated for a week after use, and it overrode any other perception powers.



No use to the Number Man, but essential for Cauldron in vetting universes and finding individuals.  Most individuals.  There were some, like the Dealer, and triple-seven, who'd escaped.



Two-nine-three.  Incapable of talking, barely able to move.  Limbless, obese.  Another key member of the staff.



No sign of interference.  The odds of the threat being an assassin dropped.



He quickened his pace, reaching the stairwell at the end of the corridor.



Second floor basement.  He stepped out of the stairwell and progressed down the main hallway.  There were rows of cells to either side of him.  Two thousand and forty-eight parahumans, each with a number, both on the wall of their cell and in their tattoo.



``You need to narrow it down,'' the Number Man said.  ``Help me find the trouble.''



His voice resulted in an outcry, the people in the cells nearest him realizing he was there, shouting, swearing, insulting him in twenty-nine different languages.



He ignored the shouting, instead extending his right hand.  ``Is it this floor?  Yes\ldots''



He extended his left hand, ``Or no?''



The faintest brush of air touched his left hand, so faint he might not have felt it while he was walking.



He turned back for the staircase, made his way down.



The third floor basement.  Here, the special case studies could be found.  Seven-seven-seven had been one.  They got a name, more space, some quiet.



He paused.  Again, a brush against his left hand.



``Damn,'' he said, meaning it.



It was on the fourth floor.



He took the stairs two at a time, moving with an uncharacteristic haste.  He also spoke, more to himself than his companion.  ``There are others who are supposed to attend to these matters.  Which suggests the escapee is \emph{smart}, is strong enough to deal with them, or\ldots as is more typical for the denizens of the fourth floor, \emph{interesting}.''



Smart, he could deal with.  Strong, he could deal with, barring certain exceptions.  \emph{Interesting} escapees, well.  There'd be degrees of unpleasantness.



He was still hurrying down the stairs as he reached the bottom.  Two doors, both heavy, stainless steel top to bottom, capable of withstanding a small bomb blast.  Only the Doctor entered the rightmost door.  The Number Man turned his attention to the door on the left, and entered his access codes, pressed his hand against the disguised plate to the right.



As security measures went, it wasn't impossible to crack, not when one considered the breadth of parahuman abilities, but if anyone who got this far decided to pass through \emph{this} door, they deserved what they got.



The deviations, the ones who didn't take to the formula, tended to fall into certain categories.  There were those who had some minor physical or mental changes; they were little different from the most extreme deviations that appeared in typical trigger cases.  Such deviations occurred a mere eighth of a percent of the time.  They weren't what he was thinking of.



The formula wasn't exact.  Though they learned more every day, there were still unknowns regarding powers.  Whatever connection the agents formed with individuals before or during a trigger event, it didn't manifest as strongly through the formula.  When the subject was stressed, their body \emph{engaged} by that distress, the connection grew weaker.



In typical cases, the agent seemed to momentarily reach out to search the entire world, \emph{many worlds} for reference material, to seize on the subject's conception of a `bird' or conception of `movement', to build up an understanding of things that didn't exist in the agent's realm of experience.



And in cases of a deviation scenario, the agent noted the physical stress and searched the subject's frame of reference for something, \emph{anything} that might reinforce what it saw as a damaged host.



For many -for ninety-three percent of the unfortunates who were so afflicted- the agent drew from plant and animal life, from physical objects, materials and designs in the subject's immediate vicinity.



But seven percent of the extreme deviant cases didn't find something \emph{physical}, and there was little to nothing to rein things in.



Such cases were not, as a general rule, released into the wild.  It would be counterproductive.  They were briefly studied, then disposed of.  The Number Man's office was in this building because he was but one line of defense against escapees and threats, even in this department.



He paused, concentrating.



As though it were penciled in the air, in thread-thin, elaborate notation, he could see the geometry and the numbers unfolding across the world around him, through the air.



He withdrew a pen from his pocket, spun it around one finger.  The notation billowed around it, and through it, he could see the movement of the pen, the plotted trajectory, the velocity and rotation of it.  The numbers clicked into place with a speed that made the rest of him, his very \emph{perceptions}, seem like slow motion.



Here and there, there were incongruities.  Painting an entirely different picture.  His companion was here, near him.  Bending the most fundamental rules.  The Custodian.



\emph{In another scenario, she would have been kept here and disposed of once we'd found a way to dissect her}.



``I know you want to help,'' he commented.  He wasn't even entirely sure if he was being heard.  ``You see it as your responsibility.  But it's best you stay behind.''



That said, he pushed the door open.



If the cells on the third basement floor were twice as large as the ones on the second floor, these were larger still.  Each was isolated, standalone in the vast, dark basement.  The space allowed countermeasures to be maintained in each space.



And here, experiment number three-zero-one-six was out of his cell.  The Number Man knew of this one.  He'd paid particular attention, once he'd heard about the peculiarities, heard about the power.



The man was only half-dressed, his upper body bare, his beard a shaggy growth, his hair long and greasy.  Showers were provided, where patients were able to make use of them, but the solitude wore on them, and few partook with any regularity.



But the part of the man was unusual was what \emph{wasn't} there.



One leg of his uniform flapped in the wake of a wind turbine used to keep two-nine-nine-zero contained.  There was no right leg beneath the pelvis, but his right foot was there nonetheless, set firmly on the ground.  He stood as if his weight rested on it.



Other parts of him had been carved away when he'd had his trigger event.  An area of his stomach, around one eye, his entire left arm.  Where they had been severed, there was only a gray plane, featureless, without shading or definition.



But the Number Man could see it.  Could see it in the physics of the way the pants leg moved, just slightly out of tune with the way it should have been flapping.  There was \emph{something} there, a disturbance.



The test subject had destroyed one wind turbine, was facing the occupant, who was hidden in shadow.



``We escape,'' three-zero-one-six said, his voice a rasp, heavily accented.  ``Together.  I stop the spirit, you take-''



He stopped, turned to face the Number Man.  The pair was separated by an expanse of a hundred feet, in an open area with a high ceiling, only the lighting around each standalone cell allowed them to see one another.



No conversation, no pleading.  Three-zero-one-six struck before he could be attacked, leaning back and then swinging, using the left arm that wasn't there.



The Number Man was already moving, the mathematical notation filling his field of vision, singing in his ears, running along his skin.  He could \emph{taste} it, virtually \emph{swam }in a clear, precise, organized outline of the world around him.



His weight shifted as he found his center of balance.  He kicked out to push himself to the left.



Three-zero-one-six manifested the strike as though his arm were exponentially larger, the attack repeated in almost infinite variations through the space in front of him, as though he were leveraging every \emph{possible} version of himself that could have been here, in this basement, drawing them together in one coordinated strike.



Concrete and steel were obliterated, and the blow carved divots into floor and ceiling both, disintegrated layers of stainless steel that sat behind and beneath the concrete of floor and wall.



The Number Man was airborne.  He'd measured the trajectory of the first hit as it carved through the ceiling, letting it slide past him by a mere one and three-quarter feet.  He angled and oriented his body to absorb the rush of wind and dust, used it to carry himself just a little further, a little higher.  His shoes squeaked as they found traction.



He chanced one glance backwards.  The attack had left a hole in the wall, the shape matching the impression that one might have made with an outstretched hand, fingers grasping, except it was fifty-two point seven six times the man's handspan.



More notation, more numbers to work with.  He could extrapolate, get an estimation of his opponent's weapon.  He'd need a point of reference\ldots



He hesitated, as though he were catching his balance, glanced briefly at the nearest cell, while keeping the test subject in his peripheral vision.



Another attack, baited so it would fall in a particular direction, not striking anything vital to Cauldron's operations.  If this test subject got the idea of repeatedly striking in a \emph{downward} direction, or striking \emph{up, } then it opened up a whole mess of problems.  There were test subjects on upper floors, and below\ldots well\ldots it was best to leave everything below to the Doctor.



He evaded the attack as he had the first, but allowed it to fall closer.  Even without looking back, he knew he had the numbers right.  The attack with the left arm was the same size each time.  The strike passed within an inch of the Number Man.



\emph{Probability, time, }he thought.  He was expending less energy on evading the attacks, now.  He focused instead on the possible attacks, the range of motion.  The notation that sprung forth put him in mind of the Vitruvian Man, expanded to encompass every possible strike that might occur.



Not seeing the \emph{future}, but rather the possible consequences that might unfold.



Now the Number Man was free to evade even \emph{before} the attacks occurred.  As a tennis player might move to cover the open court as the opponent's racket was drawn back in anticipation of a strike, he was bolting for the safe zone, the area where incoming attacks weren't as likely to fall, where his opponent would have to take time to adjust his orientation to effectively strike.



Which would be a fatal mistake on his opponent's part.



No.  Test subject three-zero-one-six didn't use his left arm.  He kicked out with the one leg that had only the foot attached.



The Number Man ducked under the strike, throwing himself forward, rolling, found his feet in the same motion.  The kick demolished whole tracts of flooring, tearing into the bottom of the stairwell.



The distance between himself and his foe was now a mere fifty-seven feet and eight inches.



Two more strikes, sweeping attacks with a fist that could gouge floor and ceiling both at the same time, and each time, the Number Man slipped by unscathed, closing the distance at the same time.



He could see the fear on the man's face.



\emph{Deimos}, the Number Man thought.  It was an old thought, a familiar thought in the same way someone might find their mother's cooking familiar, and it wasn't his voice he heard it in.



Another strike, this one coming dangerously close to two-nine-nine-zero's cell, followed by another strike in the reverse direction.



\emph{Phobos}, the Number Man thought.  First terror, then mindless panic.



The attacks were more frantic now, but that was to be expected.  The Number Man had conserved his strength, had the stamina to move more quickly.



Twice, his opponent tried to feint, to change directions mid-strike.  He caught on quickly enough to take advantage, closing the distance to thirty feet and seven inches away, then twenty feet, two inches.



Subject three-zero-one-six had two options.  One was to be clever, to claw at the ground between them and create a divide, a moat.



The other was to strike.



The Number Man forced the decision.  He calculated his movements, let one foot skid on the dusty ground, sprawled, rolling with his own momentum.



He could hear the rasp as it tore through a section of ceiling, the attack incoming, saw the probable strike zones unfolding before his eyes.  Rolled until he had his feet under him, then sprung.



The attack missed by as narrow a margin as he'd permitted for the others.



He straightened, studied the confusion and fear on his opponent's face.  Every action on his part was measured, performed for effect.  To dust his clothes off, walking forward at a measured, unhurried pace.



To not even flinch as his opponent drew his hand back.  He was still able to dodge.  Barely.



``Stop,'' he said.  ``There's no point.''



The test subject backed away a step instead.  He tensed, readying to kick out with that nonexistent leg of his.



``You'll miss,'' the Number Man said.  ``And I'll close in and strike you, using my pen and my hand.  I can see the stress points of your body, clear as day.  I can shatter your skull like a glass, and it would be an exceptionally painful way to die.''



Slowly, he saw the fight go out of the test subject.



``Why?''



``Return to your cell, and we can talk.''



``I can't.  I'm going mad,'' the test subject sounded almost morose, defeated.



``There's only one alternative, three-zero-one-six.''



``My name is Reyner!''



``You lost that name when you came here.''



``Why!?''



``Reyner died.  Maybe it was war, maybe it was plague.  But we sent our people to collect you before you passed.  Some of the collectors were like me, others more like you, made to think the way we needed them to think.''



The test subject's eyes widened.  ``You're mad.''



``Reyner \emph{died}.  This\ldots it's a purgatory.''



``I do not know the word.''



\emph{Not in his lexicon?}



``Purgatory?  A limbo.  A place between,'' the Number man said.  He advanced, and the test subject retreated.



``Between what?''



``Hell and paradise.  The mortal coil and the world beyond.  This is a neutral ground.''



``Neutral?  Can you even understand what you're \emph{doing} to us?  I\ldots I'm a child's toy, pieces missing.''



The Number Man studied three-zero-one-six.  He couldn't imagine any toy like that.  Another cultural distinction, hailing to the man's universe?



``I understand \emph{a great deal} about what we're doing to you.  I could explain the experiments, the effects on your body, as we understand them, inform you-''



``\emph{Morally}.''



``Ah,'' the Number Man replied.  ``Morals.''



Another delusion perpetuated by society.  \emph{Useful}, valuable, much like commerce, but still a delusion.  It only served its purpose so long as it was more constructive than \emph{not} adhering to those beliefs, but people often lost sight of the fact, made it out to be something it wasn't.



He'd suddenly lost a great deal of interest in this conversation.



``I have a family.  A wife and children.''



``I told you.  You died when you came here.  You left them some time ago.''



``I\ldots no.''



``Yes.  But what you're doing \emph{here}, helping us, it's going to make a difference.  It will help save your wife and kids.  When you die, we will autopsy you.  We will use what we learn to find stronger powers.  Those powers will expand our influence and help us against the true threats.''



``Threats?  To my family?''



``Yes.  To everyone.''



``You'll save them?''



``We'll try.''



Three-zero-one-six slumped, ``I can't go back to my cell.''



``I could kill you, if you wished.''



``If I'm going to die, I'll die fighting.'



``You'll only make it violent, painful.  It will be drawn out.''



He could see the man's expression shifting, the dawning realization that there was no way out.



``Did\ldots was there a chance I could have won?''



``Yes.  Luck.  A little more cleverness.  If you were in better shape, perhaps.''  \emph{My power is better at range.  Better still as I get further away, attack from other angles, in more subtle ways}.



``Then I could have escaped?  A chance I might have returned home?''



``No.  There was never a chance you might escape.''



\sectionbreak



The door slid open.  He made his way to the chair, a  laptop tucked under one arm.



The Doctor was present.  She looked weary, but her hair was immaculate, pinned into a bun.  She stared out the window at this world's landscape, so different from his own view.



``That's two escape attempts in two weeks.  We had three in the last four y\emph{ears} before that, only one successful,'' he said.



``I'm aware.''



``We'll need to change our approach.''



She turned around.  ``How?''



``We need Contessa closer to home.''



``She's required for damage control.  Too many capes who were present for the Echidna incident think they can destroy us by spreading the word about Cauldron.''



``Perhaps we stop performing damage control.  Let the pieces finish falling where they will.''



``We'd fall further behind in our agenda.''



``Undoubtedly.  But as it stands, it's only a matter of time before we're destroyed from within.  Our operation is too big and too delicate to manage like this.''



The Doctor frowned.  ``It would mean less voluntary subjects.''



``Very likely.''



The Doctor frowned.  ``And we're behind schedule, even if we ignore that.  I'd hoped to use Shatterbird or Siberian.''



``Unlikely anything would have come of it.''



``But if it had?''



The Number Man had no reply to that.  He set his laptop on the desk and booted it up.  If they had been able to leverage either of them to defeat an Endbringer, or to find why they had wound up so powerful, compared to the typical parahuman\ldots



``It seems we may have just lost Brockton Bay.''



The Number Man's eyebrows rose, though his expression remained placid, his gaze fixed on the computer.



``Skitter turned herself in.''



With that, he \emph{did} look up, meeting her gaze.  He saw the truth in her statement and closed his eyes.  Mourning one more lost possibility.



They'd lost Coil, had lost Hero, and the Triumvirate had dissolved.  They were in the process of losing the Protectorate.  Everything they'd put together, falling apart over time.



``Is it settled?''  He asked.



``No,'' the Doctor said.  ``But she turned herself in, and as far as I'm aware, there is no mischief at work.''



``Then it's not necessarily over.''



``We can't interfere.''



``I'm aware.''



``We have to take more risks,'' the Doctor said.  ``If we're going to recover from these last few setbacks.''



``What risks?''



``If we're to decipher the formula, find the strongest effects, we can't keep tempering the mixture with the `balance' concoction.''



``Creating more deviations.''



``Far more,'' the Doctor said.  ``But we found the strongest powers before we were diluting the doses.''



``We'd lose up to twenty-three percent of our potential client base.''



``We lower the price.  It's almost trivial at this point.  The only reason we set a price in the first place was to wean out anyone who wasn't fully committed.  We've supplemented virtually every other part of our operations with parahuman powers.''



``That only returns us to the issue of how we control our interests.  We can't have deviations running around, or we'll bring disaster down on our own heads.''



``I was thinking we use you in the field, Number Man.''



The Number Man leaned back in his chair.  ``Me.''



``You'd perform.  You \emph{have} performed in the past.''



``I suppose,'' he mused.  He rubbed his chin.  He needed to shave.  ``A long time ago.''



``I know you wanted to get away from that business, but-''



He shook his head.  ``No.  This is bigger than things I want.  If I can participate in \emph{this}, I can get my hands dirty.  We'll be looking for the Slaughterhouse Nine, I take it?''



``No.  The heroes are already looking, I'm not sure what we could contribute.  There are other matters to consider, and we're giving up a great deal of control behind the scenes by having you in the field, rather than working elsewhere.''



``I take it this is another risk we're taking?''



``Yes.  Increasing the volatility of the formulas, deploying you while we reserve Contessa for the more severe situations, allowing the public to discover more of Cauldron's role in things\ldots''



``Hopefully not too much,'' he said.



The Doctor shook her head.  ``Not too much.  When will you be prepared to relieve her?''



``A day or two.  Let me get prepared.''  He stood.  ``I left the data on the laptop.  Funding, the movements of key groups.''



``Thank you.''



He left the room.  His power alerted him about the Custodian's presence as he entered the hallway.  The sum of a million infinitesimal details.



It also informed him of the seam in the hallway, marking the nearly invisible Doormaker portal.  He stepped from the Doctor's headquarters to the hallway leading to his own office.



Doormaker had changed the landscape beyond his window.  An Earth of black magma and brilliant sunsets in the middle of the day, apparently.



He moved his Dali picture, sliding it to one side, and stepped into the doorway beyond.



Barring incidents like earlier in the day, it had been a long time since he had exercised his power in any serious way.



The costume, neatly folded on a shelf at the end of the closet, seemed so very small as he unfolded it.



Even the smell, it brought back memories.



\sectionbreak



\strong{1987}



The pair of them were breathing heavily.



They exchanged glances.  Two faces, spattered with flecks of blood.



Jacob carefully stepped around the expanding pool of blood.  He crouched by the body, then grinned.



The other face wasn't smiling at all.  It was grim, a stark opposite, just as their hair colors were nearly opposites.



\emph{We're}\emph{ nearly opposites in more than hair color}.



``He can die after all,'' Jacob mused.



``Yes.''



``Wasn't all that,'' Jacob mused.  He looked almost disappointed.



``Maybe not.''



``Bastard!''  Jacob kicked the body.  ``Prick!''



\emph{I'm worried he'll get up all of a sudden, even with his guts hanging out and half his blood on the ground.}



Jacob stretched, and wet blood ran down his arm as he raised it over his head.  He still held the murder weapon.  \emph{One} of the murder weapons.  It had been a shared effort.



``This doesn't end it.  They'll come after us.''



``We could lie,'' Jacob said.  ``Tell them he used mind control.''



``They won't believe us.''



``Then we run with it.  Everyone will have an idea who we are, after this, we can make a name for ourselves.''



``We \emph{have} names.''



``A \emph{reputation}.  Don't tell me you don't feel like there is something bigger, something better.  You call yourself \emph{Harbinger}.  That's all about the things to come.''



``His name for me, not mine,'' Harbinger said.



``But the idea\ldots  There's something bigger than this, something at the end of the road,'' Jacob said.



``I don't see the point.''



``But you \emph{feel} it, don't you?  The rush?''



``Yes,'' Harbinger said.



``Forget the stupid names and spandex.  Tell me your heart isn't pounding, that you've never felt more alive than this.''



Harbinger shook his head.



``We can \emph{live} this.  Together.  Every waking second\ldots''



``Jacob.''



``Jack,'' Jacob said.  He kicked King's body again.  ``Fuck it.  He always called me Jacob, practically \emph{purring}.  His little killer in training.  As if I could match up to his Gray Boy.  I want to be more than that.  Get out from under his shadow.''



``Okay\ldots Jack.''



``If it's a farce, a joke, let's run with it.  We take simple names, dumb names, and we make people quake in their shoes at the \emph{sound}.  Jack\ldots Slash.''



``I'm\ldots no.  I won't.''



Jack wheeled on him, knife in hand.



``You want to fight?'' Jack asked.  The smile had dropped from his face.



The look in his eyes\ldots \emph{hungry}.



``No.  That's just it.  I don't want to keep doing this.''



``You said it yourself.  You feel the rush, like you're on the cusp of something greater.''



``I do feel it, but I think I can get there by walking a different road,'' Harbinger said.



He could see the disappointment on Jack's face.  See the way Jack's knuckles whitened as he tightened his grip on the blade.  His power blossomed around the boy, showing possible attack vectors.  Too many.  Harbinger wasn't sure he'd survive.



He might have to throw himself in the way of the attack and kill his friend before a more serious attack could be delivered.



Or\ldots



``I'll play, though,'' he said.



``Play?''



``Make a name for myself.''



Jack smiled.



\sectionbreak



\strong{Present}



The Number Man set the costume down.  He picked up the knife.  The same one he'd used to stab King in the back, buying Jack time to open the man's stomach.



He wouldn't wear a costume.  Wouldn't do anything particularly fancy.  He'd even keep this name.  A measure of respect to an old friend.  Something to challenge convention.



Jack was his other number, his inverse.  The Number Man was working to save lives, and he killed as a matter of kindness.  Jack considered killing a matter of fact, and any life he spared was only for his own twisted ends.



The Number Man still considered the man a friend, as much as he knew that friendship was one of those ephemeral constructs.  One of the delusions people subjected themselves to, to make the world make sense.



Or maybe Jack was family.  They'd started out on the same path, after all.



Did Jack know that there was another parallel?  That the numbers and the research with Cauldron were illustrating something else entirely?



The Number Man had been gifted with powers of perception.  To see the underpinnings of the world.  In a roundabout way, he used his power for killing, for destruction.  Jack had been gifted with a power that was good only for killing, but the Number Man harbored a suspicion that Jack was more than that.



Research within Cauldron had included tinkers, drawing many conclusions about how tinkers operated.  Some were well vested in mechanical details, drawing a great deal from it to fabricate their work.  Others had little idea about the technical aspects of what they created, relying more on instinct and creativity, relying more on \emph{their agent}\emph{s} to draw up an idea of how their work would function.  It was quite possible that other capes were doing the same thing.



There was no way Jack should have made it this far on luck and instinct alone.  Not dealing with the monsters he interacted with on a daily basis.  The idea had started as a theory, but had taken on a life of its own: was it possible that Jack was drawing on the same agent that granted him his powers?  Wittingly or unwittingly?



Did he have a second set of eyes watching out for him?  Sharpening his instincts?  Giving him a sense of imminent danger or his vulnerable targets?



And more to the point: \emph{why}?



Was Jack, perhaps, in particular sync with his agent in mindset?



And if he was, did that suggest something about their motives?





