





How did the others do it?  They entered into a room and people \emph{respected} them.



Sabah walked through her territory, a black, bipedal unicorn just behind her.  She had muscle, but the stares she got were hard ones, challenging.



Was it that she'd inherited territory that Bitch had controlled, once?  Territory where people had been afraid to go outside for fear of being attacked by dogs?  She'd tried to make it clear she wasn't that kind of leader, had tried to emulate \emph{Skitter}, even, but it hadn't worked.  Gifts she'd brought in were rejected outright, or taken wordlessly, as if people thought she \emph{owed} them something for being in charge.  She'd saved people from the Teeth\ldots saved them from extortion, threats.



Not even a thank-you.



She couldn't shake the suspicion that, well, she hadn't been \emph{here} when the disasters hit Brockton Bay.  She hadn't been a line of defense between these people and the Slaughterhouse Nine, the Merchants, the Chosen, or the Pure.



She'd \emph{been} one of those people, instead.  She'd escaped being the victim, but\ldots she'd lost so many people she cared about.



It wasn't the first time she'd done this.  Gravitating towards one idea, feeling like she'd finally found the one thing she \emph{had} to do.  It was never \emph{easy}.  Always an uphill climb.



High school had been hard because she'd immigrated from Basra with her family.  She'd had an incomplete understanding of English, had been forced to learn the language as she learned the subject matter.  Her parents had been too occupied with their own issues and their own adjustment to help her out, so she'd done it alone.



Sabah was still kind of proud that she'd managed it, even if it wasn't something that anyone else had ever recognized.  A private, personal victory.



She'd attended university, and had gravitated towards the grittier subjects.  She'd taken math courses, focusing on engineering after her first year, because they had been the subjects she'd found easiest in her transition to an English high school.  She'd been okay with it, not happy but not miserable, but still, she hadn't had a person to confide in.  She'd stuck it out on her own, quietly uncomfortable with where she was in every sense of the word, unwilling to burden her family with her relatively minor issues.



Being a girl in a male-dominated field, she'd drawn attention from one student.  A boy.  He'd been nice, but he'd also been under the impression that being \emph{nice} demanded reciprocation, as though every action deserved an equal and appropriate reaction from her.



He was always \emph{there}.  They had the same classes, because they were in the same program, barely twenty-five of them in all, and Brockton Bay's college wasn't that big.  He was \emph{always} interested in talking to her, and her more demure rejections had had no effect.



She tried a clear `no', and it didn't work.  He'd gone away for a few days, then came back, making another casual hint about them maybe going out.



She tried a \emph{harsh} no, laced with all the anger and frustration she'd been feeling, and she got labeled a `bitch'.  The other students, friends or acquaintances of her would-be-paramour, wound up hearing and turned on her.  Her schoolwork started to suffer, because she didn't have the study groups, nobody willing to work with her on projects and presentations.



So, after six weeks of that, she'd caved.  She told him she'd had a bad day, apologized for her attitude.  She'd hated herself for doing it.



It only served to put her right back where she'd been before, dreading going to class and dealing with him.  Always with that vague fear that he'd escalate, that he'd start sending her emails or phoning her.



And because of the way she'd done it, she'd burned a bridge.  She couldn't defuse the relationship with a statement to the effect of, `I don't like boys.'  He would have seen it as another manipulation, and she couldn't have managed if she were cut off again.



Her father's terminal heart attack had been another straw on the camel's back.  Alone, it was nothing, but in combination with everything else\ldots Sabah had triggered on what was only one in a long string of nights spent alone, stewing in frustration, fear and anger in her dorm room.  She'd glimpsed something \emph{bigger, }something that was beyond her recall now, and she'd gained her powers.



That had been the push she'd needed to walk away from the boy and the engineering program.  She'd found a new goal.  Success in fashion design.  As far away from engineering as she could get.  Her mom had been disappointed, but she'd felt like she maybe had a direction.  She'd made friends.  Even moved out of a coveted single-bed dorm room to a double to socialize more.



It hadn't lasted long, that motivation.  Even before Leviathan came and dashed the college to pieces, she'd had doubts about whether it was what she was meant to do.



Even before the Slaughterhouse Nine had killed her mom, her aunt, her cousin, and her roommate, she'd been feeling hopeless, desperate.



She'd taken Skitter's offer, hoping that maybe, \emph{this time}, it would be different.  That maybe, if it was something she \emph{needed} to do, rather than something she wanted, she'd find that direction, find that \emph{focus}.



She hadn't.  From beginning to end, it had felt as hollow as each of the earlier ventures.



Sabah made her way to her headquarters, her \emph{atelier}, and she couldn't help but notice the way people stared, or the way they didn't show her the respect that Skitter seemed to naturally accept and respond to.



She hadn't been here when it counted.  Now they were moving on, and she was rudderless once again.



Always an uphill climb.



She'd just reached her atelier when her phone rang.  A text.



Flechette:
Skitter showed up at PRT office and turned self in.  They taking her to cell right now.



She had to reread it to make sure she wasn't getting the wrong impression.  Skitter\ldots The ramifications of this\ldots The\ldots What?



Before she could even wrap her head around the subject, there was another text.



Flechette:
You know anything about this?



The heroes seemed as confused about this as Sabah was.



Parian:
Nothing.



She found Tattletale on the contact list, tried calling.



A busy signal.



A text instead?



Parian:Tt skitter just surrendered to heroes



The reply was almost immediate:



Tt:I know. come 2 meet place from other nite asap.  First floor.



No answers, no information, only an order to meet up.



The unicorn wouldn't do, put together like it was.  It had to be deconstructed, repurposed.



Her power gave her fine control with lightweight materials.  That wasn't a problem.  Threads unwound, seams coming undone.



But her control of \emph{larger} things was an entirely different beast.  Her telekinesis fell apart when she tried to move anything heavier than a half-pound or so, her dexterity and speed in moving those objects that much slower.  Worse, her telekinesis exploded, and not even in a constructive manner.  It got more and more unstable as she tried to move larger things, until it simply\ldots expanded, dissipated over an area in an attempt to extend control to a multitude of tiny, lightweight objects.



She began reconstructing the unicorn into a quadruped.



She'd experimented, after getting her power.  Found that she could contain the telekinesis and keep it from dissipating.  It hadn't been \emph{constructive} until she started working with more flexible materials.  Porous materials worked best, because her telekinesis could soak into them, through them, and allow her to move the fabric rather than just the material within.  The gaps in the fabric allowed her to feed power into the `shell' without it building to critical mass and collapsing.  Cloth worked best.  Torn or ripped seams could be mended, any other damage proved easily fixable, compared to the issues sturdier material posed.  It was plentiful, cheap, and effective.  Cloth was her ideal material.



And once the construction was formed, a shell that trapped the telekinetic energy within until it was \emph{heavy}, she could move it as a collective whole.



The unicorn, at her bidding, bent down to allow her to climb onto its back.  Once she was securely in place, belted onto the cloth animal for security, it took off.



There was no instinct here.  It was all forced, all clumsily hobbled together with a power that probably wasn't intended for this use.  If powers even had an intent backing them up.



As such, it took time to find the unicorn's stride.  She had to watch where it put its `hooves', fashioned of work gloves and the scraps of rubber boots.  She could feel with her power, where it was, but she couldn't see through its eyes, and any coordination it possessed was limited to what she could give it from her current position.



She wasn't \emph{good} at this.  Navigating the streets, where they were congested with cars, or making her way through the areas where there was construction, littered with obstacles and pitfalls.  At being a cape, at being an \emph{important} cape.



The Forsberg Gallery appeared, and she ducked off to one side to deconstruct the unicorn.



The material formed two smaller creations, for a smaller profile, and for some muscle to move a barricade meant to keep bystanders out of the construction area around the gallery.



Tattletale, Regent and Imp were already there when she arrived, along with two of Tattletale's soldiers and one of Regent's underlings.  A television was hooked up, standing in the center of the room.



``\ldots\emph{not yet confirmed, but sources suggest that the supervillain is within a containment cell, as authorities convene to discuss\ldots}''



Parian glanced at Tattletale, who was sitting on the stairs, head hanging.  She was wearing full-coverage sunglasses over her mask.  Solemn, staring at the ground, or just resting, with her eyes closed.



``Any details?'' Parian asked.



``No,'' Regent said.  ``Nothing but the obvious.''



Grue entered, and he was a storm of darkness, to the point that his body wasn't even visible.



``Hey, big brother,'' Imp said.  There was a notable, very deliberate pause.  ``How're you doing?''



``I should have known.  Should have put it together,'' he growled the words in that voice of his that made Parian's hair stand on end.  He turned to Tattletale, ``Did you know about this?''



``Power's out of commission,'' she said.  ``Still have a headache.  Keep voices down, please.''



He didn't reply, turning his attention to the TV.



``I can't help but note you didn't answer the question,'' Regent told Tattletale.  ``Did you know?''



Grue turned back to look at her.



``Had an idea.''



``Yes, then.''



``Yes.''



``\emph{Why}?''  Grue asked.  ``Why keep it a secret?  Why is she doing this?''



``I kept it a secret because she asked me to and she's doing this because she thinks it's going to fix more things than it breaks,'' Tattletale said.  She shifted position with care, as though every movement was painful.  Even after she stopped, Parian could see her clenching her jaw, as if staving off waves of pain.



``Remains to be seen,'' Grue said.  ``Why didn't she discuss this with us?''



It was Regent who replied, ``She thought we'd convince her it was a bad idea.''



``That's \emph{not} a convincing reason,'' Grue answered.



\emph{This is the team}, Parian thought.  Skitter was always at the core of it, a group forged by innumerable challenges, each trusting the others to have their backs as they risked life and limb.  \emph{And she just betrayed that trust}.



``There's two major issues we have to deal with,'' Tattletale said.  ``Accord is going to be one.  The other is-



\emph{Bitch}.



The girl entered the room, two large dogs flanking her, the wolf cub trailing behind, unmodified by her powers.  The young American bulldog, still not fully grown, an older pitbull that bore the scars of old dogfights.  The wolf cub was comparatively small.  \emph{Adorable.  }Adorable and capable of turning into a murder machine the size of a pony.



Bitch was imposing in an entirely different way than Grue was.  Grue was intimidating, but he was \emph{fair}.  Rational.  Bitch wasn't either of those things.  Her blond hair was shaggy, having grown in, combed with little more than fingers, if appearance was any indication. The glimpses of her face that showed in the midst of the hair were a wary glower.



The girl had her jacket slung over one shoulder, otherwise wearing a simple white sleeveless undershirt with no bra.  She was muscular, but she \emph{had} to be to control the dogs when they were growing, to exert enough strength to get them to turn their heads or change direction.  Other parts of her bore similar signs of her day-to-day activities.  Her knuckles were scraped and raw, and she had a scratch on one cheekbone, taped shut.  The chain that attached to the pitbull's collar was wound around one arm.  She was beaded with sweat, likely due to the exertion of the ride coupled with the heavier pants and boots she wore.



\emph{I hate being short, }Parian thought.  To look at them, few people would have guessed there was a four-year difference in ages.  Or they would have guessed the difference in ages went the other way.



Primal, unpredictable, dangerous.  Bitch was imposing for those reasons, and because she was \emph{emotional}.  She could and would lash out with physical violence if provoked.  Even if she \emph{imagined} that someone was provoking her.  If she was \emph{really} provoked, she wouldn't move a muscle, which was worse.  She'd whistle and set her dogs on anyone that crossed her.



Parian felt her heart rate pick up as Bitch approached, felt that sense of \emph{danger} peak as they briefly made eye contact, before the girl moved on.



As unfriendly as the girl was, Bentley was friendly, the young bulldog nudging Parian's hand for a scratch before hurrying to catch up to his master.



Regent turned off the TV.  Bitch stood there, turning to look at each of her teammates in turn.



``What?''



``Christ,'' Grue muttered.  ``Tattletale.  You didn't tell her?''



``Tell me what?'' Bitch asked.  She glanced around.  ``Where's Skitter?''



Nobody volunteered an answer.



``Is she hurt?'' Bitch asked.  She didn't even sound concerned.  When nobody spoke up, she expanded her question.  ``Is she \emph{dead}?''



``Fuck it,'' Regent said, ``I'll say it.  Skitter's at the PRT headquarters.''



``So?  We break her out.''



``She went there on purpose,'' Regent said, almost offhandedly.  \emph{Carelessly}.



Parian couldn't help but notice the way Bitch clenched her hands, one gripping the metal chain until her knuckles went white.



``Regent,'' Grue said.



``What?  You don't want to deliver the news, you don't get a say in how it's presented,'' Regent retorted.



Bentley and the wolf cub both planted their feet further apart, while the pitbull was looking around, all of a sudden.



\emph{There.}  Bentley's shoulders were bulging slightly.  Bitch was using her powers.



``\emph{So}?'' Bitch asked.



``So\ldots that's it.  That's why we're here,'' Regent said.  ``We're here to talk about this, to plan.''



``She'll be back,'' Bitch said.



\emph{Will she?  }Parian couldn't help but wonder.



``I'm not so sure,'' Grue said, echoing Parian's thoughts.



``She makes plans,'' Bitch said.  ``She's smart like that.  I'm not.  I don't try to understand what she's doing.''



``She paid me a visit,'' Grue said.  ``I didn't realize it until I got the call from Tattletale.  She was saying goodbye.  Not out loud, but\ldots checking I was okay, making sure I'd be able to manage\ldots after she was gone.''



Bentley was still growing.  His flesh split at the shoulder, and he brought one back leg up, kicking at the air as if he had an itch he wanted to reach but couldn't.



The pitbull and wolf puppy were growing too.  The pitbull looked a lot less comfortable with the process than the other animals, more alarmed.  Bitch tugged the chain absently to keep him in line.



``She visited us too,'' Regent said.  ``Imp and me.''



``Me too,'' Tattletale spoke from her perch on the stairs, quiet.



\emph{Not me}, Parian thought.  \emph{Unless I count that meeting with Miss Militia and Lily}.



\emph{That served the same purposes, didn't it?  Getting things settled?  Making sure things would be okay in the future.  Ensuring the heroes could help out with my territory?}



Parian felt a sinking feeling in her gut.  Skitter hadn't been leaving for the short-term.



And that sinking feeling couldn't even compare to what the others were feeling, here.



Tattletale, nearly incapacitated.  Grue, with his darkness a virtual storm around him.  Regent and Imp, standing back, together.  And Bitch.  Stock still, radiating something more than tension.  Restrained aggression, even.



``Doesn't mean anything,'' Bitch said.



``It's telling,'' Grue said.  ``She was saying goodbye.''



``It doesn't mean \emph{anything},'' Bitch said, and her voice was harder.  ``It's a plan.''



\emph{Why am I even here?  }The thought struck Parian, out of place, out of time, a non-sequitur, yet somehow profound.  As if this point, in the middle of the discussion, was when she realized how out of place she was in the dynamic.\emph{ }



``Of \emph{course} it's a plan,'' Regent was saying.  ``It might not be a good plan--''



Bitch cut him off.  ``She goes there, she defeats them, and then she comes back.''



``Um,'' Imp said.  ``Why wouldn't she tell us?''



``She'll have a reason,'' Bitch said.



\emph{Loyalty}, Parian thought.  Misguided loyalty, blinding Bitch to the truth, but loyalty nonetheless.



``Look, it's not important,'' Tattletale said.



``It's important,'' Bitch growled.  ``You're supposed to be her friends, and you're talking about her like she's \emph{gone}.''



The pitbull seemed to take her cue, and began growling steadily.  He was still growing, his body straining against the chain harness he wore.



``She's not gone for sure,'' Tattletale said.  ``We don't know how this is going to play out, not exactly.''



Bitch didn't seem the least bit satisfied with that, but the pitbull stopped growling.  Had she stopped using her power?



``What \emph{do} we know?'' Regent asked.



``That she wanted to keep us in the dark,'' Tattletale said.  ``That she wanted to go\ldots''



``And she planned to be gone long time,'' Grue said.  ``She was asking me about leadership, about whether I was ready to take the reins.  I said no, but she did it anyways.''



``She thought this was important,'' Tattletale said.  ``Enough to put you out of your depth, as much as you don't want it, as much as she didn't want it \emph{for you}.''



\emph{I don't even figure into this}, Parian thought.  \emph{I'm not even sure I'm an official member of the group}.



``So I'm leader in the interim,'' Grue said.  There was a note of something in his voice, behind that haunting echo that his power laced it with.  Not as severe as despair, bigger than unhappiness.  Defeat?



``\ldots{}Unless there's any objections,'' he said.



Hopeful?



Nobody voiced any.



``Then we run damage control,'' Grue said.  ``Her territory?''



``We can fold it into adjacent territories,'' Tattletale said.  ``Parian, Grue, me.  Maybe the others take over some of our territories to give us an easier job of it.  She made other arrangements, with her residents.  I can contact them so we can discuss it, put it all into action.''



``Her people aren't a big priority,'' Grue said.  ``If they're not going to riot, let's put them on the backburner.  I'm more worried about anything that could go up in flames in the next hour.''



``Literally,'' Regent said.



``\ldots{}Possibly literally,'' Grue said.  ``Accord?''



``I called him just after Regent and Imp showed,'' Tattletale said.  ``He'll be here at nine thirty, on the dot.  Would have mentioned sooner, but we got caught up in talking.''



Grue nodded, glancing back towards the TV.  Parian did the same.  A number blinked on the box beneath the screen: \emph{nine twenty-six}.  ``That doesn't give us much time to organize.''



``The longer we wait, the more upset he'll be,'' Tattletale said.  ``And he's a planner.  If we give him time, he'll work out some scheme to retaliate against us.  We're stronger against him if he's on his toes.''



``Granted,'' Grue said.  He sighed, ``God, I'm not up to this.  Damn her to hell.''



There was no reply from the group.



How many members of this group were voicing silent agreement?  Parian shifted her weight nervously.  How many people here had taken a life?  All of them?  Most?



Parian couldn't help but feel out of her depth.  The terminology had never felt so apt, feeling like she was in the water, at that one point where she realized she couldn't reach safety, the water around her face\ldots



She felt like that now, \emph{here}.



Taylor had been undercover once, hadn't she?  She'd \emph{immersed herself} in this.  It was impossible to imagine.



``Accord,'' Tattletale said.



Parian thought at first that Tattletale was returning the group to the topic of conversation, but Tattletale was taking off her glasses, grimacing.



``Undersiders,'' Accord said.



``You're \emph{early},'' Tattletale said.



``Rest assured, I'm on time.''



``The clock--''



``Is slow,'' Accord said.  ``I arrived when I said I did, and I'll ask you once to please stop suggesting otherwise.''



If Bitch was an `I'll punch your face in for no reason' kind of intimidating, and Grue was an `I'll explain carefully just why I'm about to punch your face in' intimidating, Accord was something else entirely.



It was \emph{really} easy to imagine him nonchalantly standing above her while she stood in a pit he'd had dug out, a cement truck slowly filling in the space around her.  Or very politely eating someone's severed leg with a knife and fork held in the proper manner.



He was the kind of scary guy they made movies about, only he was real.



And that made her think about the Slaughterhouse Nine.



She \emph{hated} him.  She understood everything about why the Undersiders were working with him, understood that they'd be at the mercy of others like the Slaughterhouse Nine if they didn't have muscle like his on their side, but she hated him.



He was her height, dressed in a white business suit and tie, his intricate wood-and-silver mask moving to replicate the expressions beneath.



He was joined by his Ambassadors.  Each wore a finished mask, a suit for the men and a dress for the ladies: Citrine in yellow, with gemstones; Othello in alabaster white and jet black, all stark contrasts; Ligeia in a deep blue-green that contrasted her dark skin, with a conch-shell mask that swept back over the corner of her forehead, with an `up' hairstyle to match; Jacklight, with a deep royal purple dress shirt and pocket square, his mask a grinning visage that would be fitting for a child's jack-in-the-box; and Lizardtail, bigger than the others, with a green dress shirt and pocket square, an ornate mask that looked more like a Celtic knot than anything lizardlike.  Maybe the segments or spiral of it were supposed to represent a cut tail?



He'd arrived with firepower, in short.  Parian didn't consider herself very combat-savvy, but she was aware of that much.



``I\ldots rather dislike surprises,'' Accord said.



``You and me both, pal,'' Tattletale replied.



It wasn't\ldots it didn't seem like a smart way to talk to the perfectionist supervillain.  Accord was \emph{dangerous}, so why was Tattletale provoking him?



It seemed to take Accord a second to compose himself and get his thoughts in order.  ``It would be polite to stand, when a guest arrives.''



``Feeling a bit under the weather,'' Tattletale said.  ``Forgive my bad manners.  I take it you caught the essentials on TV?''



``On the radio, while we drove,'' Accord said.  ``Did you know of this scheme?''



``Of course,'' Tattletale said.  ``Do you think we're \emph{crazy?}  Everything's golden.''



``Golden,'' Accord said.



``Copacetic, peachy keen.''



``I wasn't informed of any plans.''



``You don't have to be,'' Tattletale said.



``We're allies.''



``You're \emph{subordinate }to us,'' Tattletale said.  ``If you have an issue with that, I urge you to submit a written complaint and formally declare war.  Twenty four hours notice, if you please.  I know you like rules and regulations.''



``You're mocking me.''



``Yes.  And you're \emph{letting} me mock you for some reason.  You're making a \emph{lot} of concessions in our bargain here.  You have a reason to be doing that,'' Tattletale said.  ``I'm comfortable leveraging that.''



``I made concessions because I was led to believe that \emph{Skitter} was going to be the one in charge of matters here.  I investigated her, I met her in person, and I decided she fit the necessary qualifications.  Now I'm finding that things are \emph{definitely} not what they appeared to be.  She's not in charge, for one thing, there's the reckless attack against the Teeth that saw one of my very \emph{expensive }recruits killed\ldots''



``You don't \emph{really} care about that,'' Tattletale said.  ``You wanted to wean out the ones who couldn't cut it.  Codex couldn't cut it.  Good at administration, fantastic cook, skilled when it came to managing people, and could even \emph{spar}, sure, but she didn't have the wits about her in a combat situation.  Couldn't switch gears.''



He closed his eyes, and metal shutters flicked into place as the mask mimicked the movement.  ``Please don't interrupt me.''



``I don't think you're getting my point.  I don't bend to your rules, Accord.  If you want to talk about your dead underling, let's talk.''



``She was shot in the throat from behind.''



``Are you saying I'm wrong?'' Tattletale asked.  ``About her being poorly equipped for cape life?''



``No.  The analysis is right.  I won't disagree.  But I have other concerns.  This business with how you murdered Butcher.  The girl at the bottom of the Boat Graveyard\ldots Cherish\ldots it was a risky decision.''



``Not so risky when you've done a read on the situation.  I had all the notes on Butcher Fourteen.  She couldn't teleport free, not into open water.  She still \emph{can't}, and I had a crew use a remote control device to lash a cable to Butcher Fifteen's pod.  They've dropped her into a deeper area of the ocean, and the only thing she'll be likely to kill are fish.  If we're lucky, maybe Leviathan will float that way and off himself.''



``It was risky nonetheless.  There was no assurance the plan would work.''



``And \emph{we} shouldered that risk.  Bitch and Skitter, specifically.  If it didn't work out, it was their lives on the line.''



``And now we have Skitter taking another risk.  This seems to be a \emph{pattern}.''



``She's taking the risk on our behalf,'' Tattletale said.  ``But that's not your concern.''



``It's \emph{very} concerning to me.''



``But it's \emph{not your concern,}'' Tattletale said.  There was a strain in her voice, and her fingernails were digging into her costume-covered thighs.  ``We aren't \emph{partners}, Accord.  Let's get that straight.  Do we work together?  Yes.  Have we arranged a division of labor?  Yes.  But this is our city, and you're \emph{renting} a space.''



``Tenants have rights when interacting with their landlords,'' Accord said.



``Rights, yes.  But we're supervillains.  Don't forget that,'' Tattletale relied.  ``It's our prerogative to be assholes.  And right now?  I'm going to be an asshole.  The contract stands.  Your provisions stand.''



``There's an escape clause.''



``And you're free to use it,'' Tattletale said.  ``Take the clause, leave, abandon the investments you've already made in this city\ldots''



``Or attack,'' Accord said, ``And seize everything you have.''



``Or attack,'' Tattletale said.  She sounded more tired than upset.  ``You could do that.  Or you can take my offer.''



``Which is?''



``Skitter provided your notes on managing crime in Brockton Bay.  I don't think either of us can agree to implement it, without knowing the exact outcome of Skitter's expedition\ldots''



``I agree,'' Accord said.  His interest was clearly piqued.  Parian could see the way the eyebrows of his mask had raised a fraction.



``But I like it,'' Tattletale said.  ``And if your concern is about instability within this city, I can read your work, see the solutions you propose and consider implementing them.  We would give you a hand in shaping policy beyond this group.''



``You'd agree to a contract where you implement a set number of my plans?''



``\emph{Hellll} no,'' Tattletale said.



Parian felt her heart skip a beat.  She could see Accord bristle, and his Ambassadors had tensed, as if expecting an order to attack at any second.



``But,'' Tattletale said, ``I can \emph{consider} them.  And that might be the best offer you'd ever get.  You \emph{know} your ideas are good ones.  You know there are ideas that would be worth implementing.  If I agreed to read through them, bring the better points up for discussion within the group, across our entire \emph{alliance}, and I'm hoping we recruit more than just you\ldots well, there's a chance they'd see the light of day.''



Accord frowned.  ``You're not promising anything concrete.''



``No.  I \emph{am} sticking to the deal we arranged.  This is a bonus.  It doesn't have to be big.  It's fucking generous as it stands.''



``Please be more civil,'' Accord said.  ``I'd rather you didn't swear.''



``And I'd rather you didn't storm in here and act like you were personally \emph{offended} by our particular way of doing things,'' Tattletale said.  ``I've offered you a \emph{fucking} nice deal.  Are you \emph{fucking} interested?''



``Tattletale,'' Grue said.  ``Enough.  I think he gets the point.''



``You're in charge, then, Grue?'' Accord asked.



There was a pause.  ``Yes.  But I'm standing by what Tattletale said.''



``I'll have to content myself with that, and I'll give my answer to you, as one team leader to another.  I hope to continue working with the Undersiders, and I \emph{very} much hope that things don't degenerate any further, as they have with the situation at the PRT offices right now.''



``There'll be enemies,'' Grue said.



``Yes.  But there won't be further disturbances?  Nothing further that makes national news about your group?''



\emph{National}, Parian thought, stunned.  \emph{We're national news}.



She couldn't help but think of her family, of her friends and neighbors.  Her sole remaining family member, her friend from the Fashion program.  The people who'd come to her territory for protection that she'd ultimately failed to provide.



She felt a sick feeling in her gut at the thought.  They'd been surgically altered, and, according to the most recent emails, they were getting surgery to slowly regain their old faces.  Were they watching the news right now, thinking of her?



``I'm on the same page as Tattletale,'' Grue said.  ``That's our business, not yours.''



``I see.  Well, I can hope.''



Accord extended a hand.



Parian felt her pulse quicken.  A trap?  A sneak attack?



Grue took the hand and shook it.  Parian could feel the blood pumping in her ears as she watched Accord and the Ambassadors for any sign of betrayal.



Nothing.  Accord lowered his hand, then extended it again, in Tattletale's direction.



She stood, then staggered.



\emph{Trap}, Parian thought.



Except it was only Tattletale's mental fatigue.  The villainess, with her mercenary's help, made her way to the foot of the stairs.  She leaned on the man as she crossed the room to Accord.



``Injury?'' he asked.  ``I'm thinking a concussion.''



``Migraines.  I overused my power.''



``Ah,'' Accord said.  He extended his hand a fraction further, and Tattletale shook it.  ``I\ldots suppose I can sympathize with that.''



``I bet.''



``I appreciate your willingness to meet, in light of your condition,'' he said.  ``That said, it would be best if we did not interact further.  I'd rather not terminate our alliance by being forced to murder you.  It wouldn't be polite to say how many times I came close, just tonight.''



``I think we're on the same page there,'' Tattletale said.  ``I don't want you to kill me either.  Just know that if you tried, succeed or fail, I have a \emph{lot} of questions about your involvement with Cauldron that could start circulating specific channels.''



``Ah, you're proposing mutually assured destruction?''



``Is there any other way we're going to manage this long-term?''



``No.  No, I suppose not,'' Accord said.



``Great,'' Tattletale said.  She managed a feeble smile.



``Then I wish you a good day,'' Accord said.  He managed to make it sound like \emph{fuck you}, the way people in the Victorian era might have.



That done, Accord turned to leave, marching out of the doors with his cadre of Ambassadors.



When he was out of sight, Tattletale sagged.  Her mercenary had to catch her to keep her from falling to the ground.



``Okay,'' Grue said.  ``What was that?''



``Me doing the best I could,'' Tattletale said.  ``And speak quieter, please.  My head's throbbing\ldots I feel like someone's hitting my eyeballs with hammers.''



In a marginally quieter voice, Grue said, ``You provoked him.''



``I dealt with him the only way I could.  Working with old info.  Don't even have my power, only what I got on our earlier meetings.  Shit, I haven't even read that booklet Skitter gave me.''



``Well,'' Regent said.  ``This is \emph{fantastic.  }Skitter really screwed the pooch here.''



Bitch tensed at the idiom.



``We don't know what she did,'' Grue said.  ``Or what she's \emph{doing}.''



There was a pause.



Parian had felt lost, in well over her head, since she'd set foot in here.  These guys were a group, an organization, they had their way of doing things, their rhythm.  It was so hard to jump in, to say anything.



But now, maybe, she felt like she had a role.  A reason to be here.



``I\ldots I think I understand what she's doing,'' Parian said.



All eyes fell on her.  Even Bitch's gaze, intimidating and angry.



``Generally,'' Parian said.  ``Um.  I get what she's\ldots''



``Spit it out,'' Imp said.



``She's a lot like me,'' Parian said.  ``She wants to protect people.  She's willing to make sacrifices for the people she cares about.''



``I've discussed that with her,'' Grue said.



``Terribly unhealthy,'' Regent commented.  ``Worse than smoking, even.''



``So maybe this is a way to do that,'' Parian said.  ``A way to protect \emph{all} of us.  She gives Director Tagg exactly what he wants.  Gets him to back down.  And this is how.  She uses herself as a bargaining chip.''



``I don't fucking care about Tagg,'' Bitch growled.  ``I'd rather have Skitter than have him gone.''



``It's more than that!'' Parian raised her voice, hurrying to speak before she could get lost in the jumble, unable to cut in and find a voice in \emph{their} dynamic.  She had objectivity they didn't.  The ability to see the big picture.  ``I\ldots I think she's decided on a way to help \emph{all} of us.  With more things than just Tagg.  And maybe\ldots maybe she helps herself, too.''



``Herself?'' Regent asked.



``I'm just\ldots I know what it's like, to be on a single track, to feel \emph{compelled} to keep going forward.  It isn't easy, to disappoint the people you care about, but sometimes it comes down to doing that\ldots or doing what \emph{they} want and being unhappy.''



``Unhappy,'' Grue said.



``Was there ever a time when she was with us, where she really seemed \emph{happy}?  Content?''



``I \emph{know }my brother's made her happy,'' Imp said.  ``Ick.''



Regent sniggered.



``I didn't,'' Grue said, his voice quiet.  ``Make her happy.''



``I don't know anything more than you guys do,'' Parian said, ``But\ldots{}Maybe she needs to make peace with her guilt and whatever, go to jail, and try to make amends with her dad?  If that's part of it, can we really say no?''



``What if it \emph{isn't }part of it?'' Tattletale asked.  ``What if leaving us is the last thing she wants, but she's doing it anyways?''



``Are you saying that's the case?'' Grue asked.



``No.  My power's out of commission.  I can't say \emph{anything} for sure,'' Tattletale said.  ``Except we respect Taylor--''



``We've been through hell with Taylor,'' Grue cut in.



``And we trust her,'' Tattletale said, glancing at Bitch.



\emph{So she picked up on that too}, Parian thought.



``\ldots{}So let's trust that she has an idea what she's doing,'' Tattletale finished.



Bitch moved, stepping forward, her boots making a heavy noise on the floor as she advanced.  She struck out, kicking.



The widescreen television with its tripod mount came crashing down, shattering.



Nobody spoke in the aftermath of that small gesture of pain and frustration.



They looked amongst one another, searching each other for some validation, for a response.



It was Bitch who broke the spell.  ``If the PRT fucks her\ldots''



``We destroy them,'' Grue finished.  Bitch nodded.



\emph{The most sensible member in the group in agreement with the most violent}, Parian thought.



``All we can do is wait,'' Tattletale said.



``How long?''



The question had come from Bitch.  She was tense, rigid, her jaw set, eyes narrowed.



``Nightfall,'' Tattletale said.  ``We wait until the sun sets.  That's the only instruction Skitter gave me.''



``What are we waiting \emph{for}?'' Grue asked.  ``A signal?''



``If we \emph{don't} get a signal,'' Tattletale said, ``We act.''



\sectionbreak



Parian's thoughts were buzzing with possibilities, more details, more responsibilities.  Taking on more territory, giving up some to Grue.



Still struggling to find a way to be \emph{relevant}.



She reached her atelier and dismounted from the six-legged horse, stepping down to the floor of the alley.  It had been a little more stable than a four-legged unicorn.  She'd have to refine the idea, find a balance.  Specific forms for specific tasks.



She was behind.  Behind in her territory, behind in applying her powers to combat situations, in being able to understand and interact with people like Accord.



And until she figured those things out, she couldn't truly be a part of the Undersiders.  And if she wasn't a real member of the group, she couldn't change anything where it really mattered.



The unicorn came apart into scraps of cloth.  The individual scraps rolled up, were neatly tied by braids of thread.  She lifted the largest bundle and made her way around the corner to her front door.



\emph{Ten and a half hours before sunset}.  That was the deadline.  Skitter's deadline, and the point that would determine whether this became an all-out war against the PRT or something entirely different.



Parian stopped in her tracks.  Lily leaned beside the front door, in full costume as Flechette.  The stainless steel shoulder-rest of her arbalest sat on the ground, and she used a single fingertip to keep the weapon upright, unloaded and pointed at the sky.



With a flick of a finger, Lily made the thing spin, stopped it, spun it the other way around.



``You know where I live,'' Parian said.



``The \emph{PRT} knows where you live,'' Lily said.  ``It's on record.  But we're not supposed to act like we know.  I thought you'd forgive me that, given our history.''



``Is there news?  About Skitter?''



Lily shook her head.  ``They asked me to go out and make a phone call, outside of Skitter's range.  But they didn't seem to know how far that was, so I\ldots''



``Made your way to the far end of the city,'' Parian said.



``Yeah,'' Lily said, just under her breath, looking down at her weapon.  Again, she spun it.



``You didn't even know I'd be here.''



``You weren't.  I just got an angry call from Miss Militia,'' Lily said.  ``Been out here for a bit.''



``For\ldots''



``Thirty minutes.''



``Ah.''



Parian put the bundle of cloth down, resting the end on the ground.  After a moment's thought, she leaned it against the wall by her front door.  By Lily.



She felt so conspicuous.  She knew Lily hated the black costume, with the black hair, the black dress.



Lily, who'd been maybe the only person to give her support without being asked.  Lily, who was\ldots chivalrous.  Gallant.  Stubborn.  So very stubborn.



``Did you come here for a reason?''  Parian asked, in the same second Lily asked, ``Where were you?''



``You first,'' Lily said, after the momentary confusion.



``Why did you come here?''



``Don't know,'' Lily said.



``That's a hell of a reason to wait thirty minutes.''



Lily glanced left, then right, as if looking for bystanders.



``This area isn't occupied,'' Parian said.  ``My atelier is the only one on the block that you can live in.  The rest are sealed up.''



``Atelier?''



``Workshop.  Studio.  Only fancier.''



``Ah,'' Lily said.  Then, as if she remembered why she'd been looking for bystanders, she let herself slide down until she was sitting with her back to the wall.



``That's it for answers?'' Parian asked.  ``Don't know?''



``No.''



``Just talk me through what's going through your head.  Doesn't have to be relevant.  Don't have to censor your thoughts.''



``Definitely have to censor my thoughts,'' Lily said.  She glanced up at Parian.



She felt her heart rate pick up with that, oddly enough, just like it had with Bitch.



Except Lily wasn't dangerous, was she?



``\emph{God}, I hate this city,'' Lily  said.



``It's\ldots a hard city to like,'' Parian said.  ``But it's not a city that lets you throw it away.  It's tenacious, both in the big picture, and in how it attaches itself to you.''



``Yeah,'' Lily murmured.  ``Before I came here, everything was on track.  I could see my future ahead of me, straight as an arrow.  Career path, eventual Flechette action figures.  Every single one of my teachers and superiors seemed to know I had potential.  One of the only people who could hurt an Endbringer\ldots''



Lily raised her unloaded arbalest, aimed it, ``Pow.  Critical damage every time, and I don't miss.''



``I remember what you said when you talked to Skitter and Miss Militia.  You don't feel so confident, now.''



``I've been trying to think of where I might be comfortable.  Where I could find what I've lost.  During the whole post-Leviathan thing, I was always most comfortable here.''



``\emph{Here}?'' Parian looked over at her Atelier, an unassuming, simple building.



``With you.''



``Ah.''



``And\ldots fuck me, because I'm not acting confident.  I \emph{told} myself I'd act confident, but\ldots I'm blowing this.''



``Don't stress so much about acting,'' Parian said.



She reached up and detached her mask from the metal frame that held it over her face, then pulled the wig off as well.  She let them fall to the ground.



A pure white mask, in contrast to her own Arab ethnicity.  She'd meant to make a point of it, to challenge people to wonder more about what was behind the masks, about their assumptions about heroes and villains.  That had fallen apart when Leviathan and the Slaughterhouse Nine had derailed her plan to unmask herself and start a career as a fashion designer.



More than the fashion designer part, it was the sudden recollection of what the Slaughterhouse Nine had done that took the wind from her sails.



She tipped over the roll of cloth and then seated herself on it, facing Lily.



Belatedly, she said, ``We act too much.  Hide behind masks way too often.''



Lily looked around to double-check, then removed her visor.



``I don't think I can do this,'' Lily said.



``Do what?''



``I don't know.  But whatever it is, I can't do it.''



``I know the feeling,'' Parian replied.



``Where were you?''



``You don't get to ask that,'' Parian said, quiet.  ``Just like you don't get to act like you own me, to say that my costume is anything but my choice.''



``You remember that,'' Lily said, looking down at the ground.



``Hard to forget.''



``Skitter asked me what I wanted,'' Lily said.  ``I gave her my answer.''



``You wanted me.''



Lily nodded.



``I've already had someone try to claim me, you know,'' Parian said.  ``They thought that I was something that was \emph{owed} to them, because of what they'd done.  That being nice meant I was obligated to accept a date.  And that line of thinking goes one step further.  They think flowers and a few dates mean I'm \emph{obligated} to come over to his apartment to spend the night.''



``That's not what I'm doing,'' Flechette said.



Parian didn't answer.



``I mean, it's not\ldots my motives aren't\ldots''



``Carnal?''



``Sketchy,'' Flechette supplied.



``That doesn't make it any better.''



``No,'' Lily agreed.  ``\emph{Fuck}.  I was hoping this would go better.''



``And\ldots I'm not so sure your motives were pure.  I've seen you sneak glances.  For someone who has a superpower that gives her enhanced timing, I'd think you'd be better at it.''



Lily turned red, very deliberately not looking at Sabah.



``Once bitten, twice shy,'' Sabah said, almost to herself.  ``I've been bitten once.''



``Is that a no?''



``To?  You haven't asked me anything.''



Lily shifted her grip on her arbalest, then set it on the ground, spun it on the end again, as though it were an oversized top.



``Skitter asked me for what I want.  What do \emph{you} want?''



``Direction.  No, not even that.  It's almost like I don't care as much about what I do, as me feeling like I want to do something \emph{well}, but I can't.''



The Japanese-American girl frowned.  ``And \emph{this} is what you want to do?''



``Yes,'' Sabah answered.



``\emph{Why}?''



``Because it's the only way to get the rest of the money that my people need.''



``Your people?''  Lily started to glance around, then stopped.  ``Not \emph{these} people.  Your family, friends.  From Dolltown.''



Sabah nodded.  Her heart was heavy with the thought alone.  ``And because I need to be a part of the Undersiders if they're going to listen to me, and I need them to listen to me if I'm going to influence them, keep them on a straighter path.  To protect people from them, and to protect \emph{them} from \emph{themselves.}``



``And that's all worth giving up the life you want to lead?''



Parian thought of Skitter.  Of the motivations that could be driving the girl to turn on her friends.



``I think it is.''



``Then\ldots would you take me along for the ride?''



Sabah glanced at Lily.  Lily was staring at her, an intense look.  Scary in its own way, but not quite in that way that was a reminder of uglier days.



``No,'' Sabah answered.  ``I don't think I can.  It's not that I don't trust you, but\ldots''



\emph{But I don't trust you}.  \emph{I can't have someone try to possess me, to control me}.



She couldn't find a graceful way to say it, and she could see the pain on Lily's face, the doubt, the embarrassment, as the pause lingered.



Then Lily seemed to compose herself.  ``Not as a partner.''



``No?'



``I meant, um.  A lieutenant.''



``A lieutenant?''



``I'm not good at being alone,'' Lily said.  ``I found that out a while ago, and what's happened these past few weeks, they only made it clearer.  I need company, and your company is what I want the most.  I can't say it'll be forever, but for \emph{now}\ldots''



Being together\ldots having a helping hand where it counted.  Having firepower and authority both, to help win over the locals.  It wasn't perfect, it wouldn't be fast\ldots



But maybe it wouldn't be such an uphill climb.



``You'd leave the Wards?''



``They're falling apart anyways.  I'd\ldots I'd have to give up my arbalest.  Without tinker maintenance, it won't keep working.  But I always liked the idea of the rapier, been meaning to go back to it.  And I have darts.''



``You're rambling.''



``I'm terrified,'' Lily said, meeting Sabah's eyes.  She looked it.



\emph{She's taken a leap of faith, and she hasn't touched ground}.



``You're saying I call the shots.  You're my lieutenant, my right hand?''



``Yes,'' Flechette said.



``My knight in shining armor.''



``I'd need a new costume, and a new name, probably.  For legal reasons.  If you said yes.  I was thinking more a stylized musketeer look than a knight, but I can work with whatever.''



\emph{Still rambling}.



``A new costume is something I can do,'' Sabah answered.  ``And yes.''



``Yes?''



``Yes,'' Sabah said.  ``You'll be my lieutenant.  And you're okay with that?''



``That's\ldots what I'm offering.  The last thing I want is to make you uncomfortable.''



``That's good enough,'' Sabah said.  She stood, approaching Lily.



\emph{Needle and thread}.  Somehow it felt more \emph{right}, more solid, than any of the paths she'd started on, only to later abandon.  Maybe because she wasn't doing it alone.



She put two fingers to Lily's chin, raising it, and then she kissed her lieutenant.





