





``I expect I'm not doing myself any favors,'' the girl spoke.



``Favors?''



``Remaining silent.  You're here to judge me, and silence is damning.''



``I'm not so sure I like the word `judge'.  Evaluate is a better word.  \emph{Listen} is better still.  I want to listen to you, because I can't help you if I don't understand you, and I want my understanding of you to come from \emph{your} words,'' Jessica Yamada spoke.



``Silence says a great deal, does it not?  I recently heard a man speak to the people in charge about the homeless, the masses of refugees we are still trying to find homes.  He spoke of needs, of women and children, and of families that have been broken because temporary shelters don't allow the men within.  He proposed a plan, then justified it with a diatribe on humanity and pity, leadership and the threat of unrest, the threat of people manifesting powers, and he talked of faith.  He finished on that note.  Do you know what point the canniest people in the room are left paying attention to?''



``You were talking about silence.  Something the man \emph{didn't} say.''



``You \emph{are} paying attention,'' the girl said, sounding mildly surprised.



``It's my job.''



``Then you're already aware that what one leaves out is as telling as what they include.  The \emph{void} in our speech, if you will.  The gaps.  The man said nothing of resources, of food supplies, because he does not want to raise the topic, and he has no answers there.  Silence can be louder than words.''



The therapist nodded.  ``It's an interesting thought, and it's one we could talk at length about, but, please excuse me for saying so, I think you're dodging the question.''



``\emph{Dodging?}''



``Evading, avoiding-''



``I was not asking for clarification, doctor.  I was expressing \emph{indignation,}'' the girl said, stressing the last word.  There was a kind of \emph{vibration} in the words as she said it.



``Whatever else you are, you're still human.''



``There was a time I'd have swiftly responded to that,'' the girl said.  ``You would be dead, if you were fortunate enough.''



``\ldotsAnd you're acting like I should be able to read something in your silence.  The problem is that speech needs periods of silence to be intelligible, to separate the words and keep it from being a steady drone of noise.  To frame it.  The opposite is true.  To find the meaning in what's left unsaid, we need words to punctuate it.''



The girl opposite Jessica Yamada frowned just a little.  Her deep green eyes didn't move a fraction as she met the therapist's.  It held an intensity that suggested she could have faced down a stampeding elephant or an airborne missile.  Very reluctantly, she said, ``\ldotsFair.''



The therapist relaxed a touch, sitting back in her chair.  ``What we do here is up to you.  I've had patients who enjoy this kind of verbal jousting.  Many walk into a first session with preconceived ideas, that they'll be forced to lie on a couch and bare their vulnerabilities while I pry at them with questions.  A debate gives them their power back.''



``It's the approach that makes sense.  The, er,'' the girl stumbled uncharacteristically as she searched for a word, ``\emph{parahumans}\ldots they tend towards conflict.''



``There is a lot of evidence to suggest that's the case.  Do you?  Tend towards conflict?''



``No.  Which is a good thing, I imagine.  My other half was always more patient, more relaxed than most.  Its duty was always at the \emph{end}.  For those who had duties at the \emph{beginning, }it would be harder.''



``How do you define beginning and end, when it's a cycle?''



``Beginnings and endings,'' the girl mused.  She smiled a little.  ``I'm tempted to say you just \emph{know}.  That it's instinctual, you \emph{know} what you are.  But that's something of a coward's answer.  More correct to say that you can distinguish the two when there's a long, long journey in the middle.''



The therapist shifted her position, taking a glass of water from the table beside her and sipping it.



\emph{No doubt inviting me to keep talking}, the girl thought.  She turned her attention to her drink.  It was cold.  She exercised her power, reaching into the deep dark well within her, and withdrawing a single individual.



P\~{o}letama, the firesinger.



The individual emerged, coalescing from shadows.  A woman, dark skinned, with skin painted in wild colors that had once hidden her features as well as any mask.  Where it had once been paint and flesh, the barest minimum of cloth, the flesh ridged.  Her eyes burned as she stared out from the shadows of her deep-set eyes.



The girl didn't take her eyes off the therapist as the firesinger reached out and put one glowing fingertip into the water.  It took a moment for the liquid to start steaming.



The other two shadows stood at different points in the room.  One stared at the bookshelf, its lips moving as it murmured in a voice only the girl could understand.  The other stood at the window, arms folded, his cape moving in a wind that wasn't present, hood hiding his features.



The girl in the heavy leather chair, by contrast, wore only a sleeveless top and a knee-length skirt.  Both the collar of the top and the skirt had heavy lace at the edges.  Her blonde hair was braided.  It made her look far younger than she had in previous appearances, and she'd looked young then.



``You were tempted to say you instinctually know who you are,'' the therapist said.



The girl tilted her head a fraction.



``To be blunt, I'd say the vast majority of my patients don't know who they are.''



The girl lifted the steaming mug to her lips.  The smell of the heavily spiced mead flooded the room. The therapist didn't comment, hadn't commented.  She was \emph{technically} legal, however young she might look.



The girl swallowed, then said, ``\emph{What}, not who.''



``It's the same thing, isn't it?''



``Perhaps,'' the girl responded.



The therapist spoke a little slower, as if she were testing her words in her head before she spoke.  Exceedingly careful.  ``You seemed to know who or what you were, before, and you changed your mind.''



``People are allowed to do that.  To change.''  The response was dismissive, cavalier.  All such a statement demanded.



``Do you consider yourself \emph{people}, then?  Just a minute ago, you said you would have taken offense to the idea.''



``You harp on.  These are all variations on the same question,'' the girl said.



``Yes.  Who are you?  How do you see yourself?  Has that changed?''



``I am very possibly the strongest being alive on this planet, short of the remaining Endbringers.''



``Very possibly.''



``A murderer.''



``In what sense?'' the therapist asked.  ``One who has murdered, or one who murders?''



``Same thing, isn't it?  You don't leave that behind you.  Nobody lets you.''



``People can forgive and forget.''



``They might forget murder, they might forgive madness, but they won't be so ready to make peace with a lunatic murderer,'' the girl said.  She sniffed a little, as if scoffing at the thought.  ``You wanted to know who I am?  I was perhaps Scion's greatest ally, until\ldots I wasn't.''



``Why weren't you?''



When the girl spoke, an echo had creeped into her voice.  A chorus.  ``You know, I could kill everyone, if I so chose?  If I decided to stand, right here and right now, and kill you all, it would be fully within my power?''



The therapist didn't flinch.



``Do you doubt me?''  The chorus was there in full.  A hundred voices from one mouth.



``To be honest, I don't know enough about the combat side of things to say,'' Ms. Yamada said.



``It's cause for any sane person to worry for their welfare, and for the welfare of their loved ones.  You pretend indifference.''



``I'm anything but indifferent.  I'm genuinely more interested in the fact that you seem to be avoiding the subject.  A subject \emph{you} raised.''



``I grow irritated with this pedantry,'' the girl said.  She stood abruptly from the chair.  Two of the shadows dissipated into smoke.



\emph{Prolapse, torturer's son.}



\emph{P\=h\textoverline{u}\^ comt\textoverline{i}, rider in daylight.}



The two new shadows took their place on either side of her.  Big individuals.  Villains, once upon a time.



The therapist continued, ``You've stopped calling yourself the Faerie Queen.  When I asked for a name, you stayed silent, and you sat there for nearly twenty minutes before talking.  You could have helped Scion and destroyed us all \emph{then}.  You didn't.  I'm asking you what happened.  It's clearly important to you.''



The girl's eyes didn't waver, but she lowered her chin a touch, and the angle of her head cast her features in deeper shadow.  When she spoke, the choir of voices that came from her mouth was calm.  ``Do you have a preference, in how you'd like to die?  I have a range of powers at my disposal.  There are swift methods, but perhaps you'd like to go out more dramatically?  If you beg for mercy, I could spare others.''



``You're allowed to say you don't\emph{ know }the answer, Ciara.  If it comes down to that, then I can suggest an answer and we can explore it together.''



The girl had gone still.  Her shadows were flexing, one cracking knuckles on a hand roughly the size of the therapist's entire upper body.



The girl considered the visuals of crushing the therapist, the way flesh would pulp and seep between the shadow's great fingers.  It was a good alternative to dwelling on the feelings that had just stirred.



``Nobody has called me by that name in a very long time,'' the words were more a threat than anything.



``It was in the records,''  Ms. Yamada said, ``I need to hear the answer from your lips first, before I can offer you my thoughts.  But let me warn you, I'm only offering a suggestion.  Food for thought.  I read the transcripts from the debriefing you gave Chevalier.  You talked about anchors.  I don't want you to\ldots `anchor' to anything I say.  Use it to find your own answer, instead.''



``You claim to know me better than I know myself.''



``We'll discuss that point if and when we get that far.  For now, I need to know \emph{your} thoughts on what happened.''



``I-''



``But please sit down, first,'' the therapist said.  ``We both know you could kill me at any moment, here.  Having \emph{them} here doesn't change that, but it's\ldots''



``It \emph{is} admittedly vulgar,'' the girl supplied.



The therapist nodded.  ``We'll go with that.''



The shadows dissipated.



\emph{Ampelos, the ill-fated.  I was the ill fate.}



\emph{Daimones, the lost.}



The ones who replaced them were children.  One, young enough to be androgynous, wore a long-sleeved shirt that hung down to its knees.  It spun in place, skipping, then spinning again, a toddler at play.  The other explored the room.  The man with the hood and cape remained by the window, arms folded, staring out at the world beyond.



Ciara spoke.  ``He broke.  He was strong, he was noble, proud.  He was a monster, alien.  They brought out the humanity in him, and then they broke him.  I could have stepped in, but I didn't.  I don't know why.''



The words were a challenge more than an admission.  A demand for a better answer.



``Would you like to hear my theory, then?''



``As you wish,'' Ciara replied.  She didn't quite manage to feign the indifference she was going for.



``You're exactly what you appear to be.''



``What do I appear to be, doctor?''



``An adolescent.''



Ciara frowned.  ``I had hoped for a \emph{good} answer.  I'm older than \emph{you}.''



``Only just.  Chronologically, I think we're the same age, nine months apart.''



``You miss my point,'' Ciara said, clearly annoyed.



``No.  I got it.  Chronologically, you're older, and by those measures, your youth is only a mask you wear.  By \emph{other} measures, you're still a child.  You triggered at a very young age, you were no doubt isolated, as masters tend to be.  No doubt surviving purely by your own methods.  Somewhere along the way, something happened.  You stole the wrong power, you fought someone and lost, or you found yourself in a bad situation.  In the course of that event or in the wake of it, you unlocked stronger powers, and they eclipsed you as a person.  Am I too far off track, here?''



Ciara didn't respond.  Her hard stare was a challenging one, now, a \emph{hard }stare.



``You were still a child, and you needed rules and a foundation to define yourself by, as any child does.  Your chose your anchor, chose Scion, and you formed your view of capes as faerie to distance yourself from a world you barely felt in touch with.  You built up your persona as Glaistig Uaine, a name others gave you.  It might have even played a role in why you turned yourself in and took up residence in the Birdcage.  You craved \emph{structure}.''



``You're calling me a child?''



``I'm \emph{suggesting }you were functionally a child until a very short time ago.  You're now an adolescent.  Scion was a powerful figure in your life, owing at least partially to your power's involvement in your day to day, minute-to-minute existence.  Virtually every child goes through a phase where their parents are invulnerable, incapable of failure, strong, and beautiful.  They grow out of that phase when reality challenges that assumption.  If what I'm suggesting was true, well, reality never challenged the assumption because it was \emph{true}, in Scion's case.''



``Up until the moment he began to lose,'' Ciara said.



``Many begin to rebel against their parental figures around the time they enter adolescence, around the time they start seeing their parent as flawed \emph{humans}.  In your case, it was a faster process.  A moment's decision.  Whether I'm right or not, you were thrust into a new mode of thinking, a new mode of \emph{being}, and it has to be bewildering.''



``Your theory, then, is that the most powerful cell block leader of the Birdcage was a mere \emph{child, }however old she might have appeared?  That the answer to my present crisis in identity is that I am a mere \emph{teenager}?''



``For the adolescent, the greatest, most defining challenge is to find themselves.  To seek out identity.  For the unpowered youth, it's often a question of what clique they fit in, what clothes they wear, how they express themselves, and what path they want to step forward on, in terms of possible careers.  For powered youth, it's about all of the things I just mentioned, as well as the villain and hero labels, their place on the team, their place in family, the bonds they form.  These are questions you're now asking yourself.  Am I wrong?''



``I dislike being painted with such broad strokes, doctor,'' Ciara spoke.



``There are \emph{always }variations,'' Ms. Yamada said.  ``I'd never approach a patient with the idea that it comes down to this and this alone.  It's a starting point.  You need to find yourself, and you need to do it with the burdens of the strongest human being on the planet.  I'm telling you, here and now, that this is something \emph{everyone} faces at some juncture.  It's perfectly alright to define yourself as `someone who is looking for definition'.''



The girl smiled a little.  She lifted her mug to her lips, then wiped her mouth with her thumb.



The therapist took another drink of water.  ``You're smiling?  I suppose I don't need to worry about my impending death, then?''



When Ciara spoke again, her voice was normal.  ``What you said is\ldots a thought.  I was smiling because I was wondering what your superiors would think if they knew what you'd told me.  A powerful parahuman, free to \emph{find} herself?  Perhaps I'll follow in the footsteps of my `parent'.''



``I don't have any superiors,'' the therapist said.  ``The PRT is done.  There are groups trying to cobble together a replacement, but it's looking shaky at best.  I'm here because I was invited, and because I want to help people.  I'd like to help \emph{you}.  I think everyone would be much happier if we found you a path that isn't following in his footsteps.''



``Did I ask for your help?''



``You're still here,'' Jessica Yamada said.  ``Y-''



She didn't get further.  There was a knock on the door.



The concern on the woman's face, Ciara noted, was more than it had been when she'd been threatened with her own imminent death.



``Please excuse me.''  The woman stood from her chair and crossed the room.  She opened the door.



Ciara watched as the figure unfolded before her.  A giant armored in the skin of a monster, a knight, a wisp of a figure, all at once.  She could see his very \emph{presence} tearing through the doorframe, the slightest movement tearing whole sections of the building to rubble.  She could feel the vibrations, taste the dust in the air.



But that was only one version of the building, out of sight, out of mind.



As if she was squinting without moving her eyelids, she refined her vision, saw him as the therapist saw him.  A man in gold and black armor.



His voice was barely audible.  ``Ms. Yamada.  I'm sorry to int-''



``I'm in a session, Chevalier.  An \emph{exceedingly} important session.''



``I know.  I'm really very sorry.  I had a small opening in my schedule.  I was hoping for just one minute to talk with you.''



``I'm \emph{in a session}.  You agreed to abide by any rules I set.  This was a pretty big one.''



``If I didn't talk to you now, I'd have to wait three days to get another chance.  My hands are full.''



``I can imagine.  But I'm in a session.''



``One minute.  Trust me when I say I know how important it is that you stick to your rules.  But this is important enough that I have to ask.  Can I have one minute of your time?''



The woman hesitated.



``Please.''



The therapist turned, meeting Ciara's eyes.  ``No, Chevalier, I-''



``I'll manage on my own,'' Ciara said.  ``In fact, I would appreciate having a minute or two in private to think over what we talked about earlier.''



Ms. Yamada frowned.  ``I'll be back shortly.''



The door closed.



\emph{Roucouler}, \emph{the Liar.}



The little girl that was exploring the room dissipated.  A man appeared behind Ciara's seat, his leering grin stretched into a caricature, a mockery of what he'd worn in life.  His teeth had no divides between them, making them one bony shelf, and his eyes were stretched into slants by the too-wide grin.  A cartoonish appearance.



Roucouler leaned over the top of the chair, and she could hear his whispers, in a French accent.  He pitched his voice to distinguish between the two.



``\emph{-cohol in there?''}



``\emph{She had her shadow make it for her.  She's not the type to get drunk, and it's more of a comfort thing than anything else.}''



``\emph{A bear walks into your restaurant.  What do you serve him?  Anything he damn well wants.''}



``\emph{There is that.  What do you want, Chevalier?  This is nerve-wracking enough, without interruptions.}''



\emph{``Did something happen?''}



``\emph{I can't talk about my sessions with my patients.  If we're going to talk, let's talk about your business.}''



``\emph{I'm running out of time.  Three days from now is too long to wait, because things take time to set in motion.  I'm going to have to start making decisions, about amnesty for everyone who participated in the fight, about the hero teams, how we're going to administrate a city that has more sheer depth than anything we've ever conceived of.  That woman, in there, she's at the crux of this.  Choices I make in regards to her affect everything else.  If I forego amnesty for her, if I have to forego amnesty for her, then I'm drawing a line in the sand, and others are going to wonder if they fall too close to that line.}''



``\emph{I can't tell you how the session is going, Chevalier.}''



``\emph{I hate that you even have to say that.  I'm not going to ask you to violate any confidentiality.  I'm saying I could really do with you making your evaluation and then sending her on her way.  There's apartments here, we can set her up very comfortably.  As comfortably as a queen might want.  If she needs further therapy, you can send her there.  If she's stable enough to discuss business, be it amnesty or something else entirely, you could send her to me.}''



``\emph{I understand what you're saying.  If she's dangerous enough to warrant violating confidentiality, it doesn't matter.  If she isn't, then I can let you know how the therapy went without explicitly telling you.  I'm not entirely comfortable with this.''}



``\emph{There have been more overt communications on this front}\emph{in other situations.  Situations that weren't so grave.  We can't afford not to know.}''



``\emph{I can't afford to tell you, Chevalier.  I just\ldots let me think on it.}''



``\emph{That's all I ask.  We need help, Jessica.  I know you can't make a full judgement in three days, not with someone as\ldots complex\ldots as she is.  But a starting point could make all the difference.}''



``\emph{I understand.}''



``\emph{We're putting the pieces back together.  The scale of it is the biggest issue.  All these worlds.  There's room for people to start piecing their cultures and their cities back together, there's wilderness.  Everything old is still there.  Sometimes multiplied many times over.  But there's a lot of new, with more every day.  It's all exaggerated.  We don't have clout, and there are a lot of powerful people throwing their weight around.  Scary people.''}



``\emph{Speaking of\ldots}''



``\emph{Your patient, I've kept you too long.  I'm sorry.''}



``\emph{No.  I'm wondering about someone who was a patient some time ago.  Can I ask about this `Khepri'?}''



``\emph{You can ask, but you won't like the answer.  I wouldn't want you to be distracted for the remainder of your session in there.}''



Ciara heard the Liar sigh, mimicking the woman on the other side of the door.  ``\emph{I'll take your word on that.  I should get back to Ciara.}''



``\emph{Ciara?  Her civilian name.  I'm going to walk away feeling optimistic about that.}''



``\emph{My lips are sealed, Chevalier.}''



There was no goodbye.  The door handle moved, and the door swung open.  Roucouler disappeared.



\emph{Pime} Abtiss, mother\emph{of the blind.}



Another shadow appeared as the therapist entered the room.  A blindfolded woman with a small, deformed baby in her arms, umbilical cord stretching into a gap in the robe.



Ciara could see a glimpse of the giant in the hallway, retreating, before the door shut.



``I'm very sorry.  That took longer than I expected,'' Ms. Yamada said, as she took her seat.



``No matter,'' Ciara said.  She ran her hand over the baby's misshapen head.  It dissipated into shadow, along with \emph{Pime Abtiss}.  She didn't replace it with another shadow.  ``Forgive me, I overheard.''



The therapist reacted a little to that.  There was a moment's pause, as if she was recalling everything that was said, searching for any damning detail.



``I'll spare you the dilemma, doctor.  When we are done, tell me where I should go.  I relieve you of any confidentiality, tell the Destroyer what you must.''



``I don't think that's what we should aim for,'' the therapist said.  ``If we go with my theory from before, then you've only just started making strides on your own.  You're growing up, belatedly, and you need to start making choices for yourself.''



``You'd let me choose?''



``I think a better place to start would be figuring out who you want to be.  That \emph{equips} you to choose, if you feel you're ready.''



``And what if I were to say you're being \emph{presumptuous}, that I don't need your help?  I know who I am?''  There was a threatening note to the girl's voice, a return of that echo.



``Then we can talk about something else.  Or you can go, if that's what you really want.''



Ciara didn't move, and her shadows remained in place, poised like animals ready to pounce.



While the girl remained still, the three shadows resumed their ordinary business.



``Let's begin, then,'' Ms. Yamada said.



\blacksquare



The rooftop was lined with crenelations and a wrought metal railing in a metal darker and stronger than iron.  Some capes rested in the spaces between the twists of metal, while others sat with their backs to the shorter wall beneath it.  The crowd had gathered around.



But the moment she relaxed, it became something else.  Phantom images, a man on fire, a woman who stood half again as tall as others.  Images like her own shadows, caricatures, exaggerations, powers manifested physical.  Except these were undoubtedly \emph{alive}.  They shifted from moment to moment.



``Legend?'' the Destroyer- \emph{Chevalier} spoke.  His voice echoed, but despite the massive size of his one suit of armor, or the slight form of his other suit, mangling the body within, the three voices were the same, only coming from different places.



A man who blazed with light stepped forward.  He was a living bonfire, blue-white in color, with living etchings solid in the midst of it, white hot, a stylized mixture of flame and lightning in one shape, floating in the storm of energy.  They marked the position of his head, of his chest, his hands and feet.



When the Coruscant Knave spoke, though, his voice was normal.  \emph{Legend}, she reminded herself.



``I was there at the beginning.  I suppose it's fitting that I'm here at the end.  Maybe not \emph{right}, there's a hell of a lot I'm sorry for, but it's fitting.''



He took a deep breath, the flame swelling.  ``They say a picture's worth a thousand words.  Let's shorten this speech, then and take a second to \emph{look}.''



He gestured, and heads turned.



New York, in the process of being rebuilt.  Dust and ominous clouds were being held at bay by a thin forcefield, and the city stood in the center of a brilliant sunlight.  Where glass had broken and where oils had risen to the tops of city streets, things almost glittered.  A shining city.



For every damaged area, there were people, fixing things, scavenging and hauling things away.  Tents and tarps were erected, barriers raised.  Already, buildings were going up where portals had been torn between realities.



Chevalier had called it a city with depth.  It was true.  Most cities existed on a two dimensional level, spreading along the four cardinal directions.  Buildings extended above and below ground, but even the tallest building was but a fraction of a distance compared to the \emph{breadth} of the city.



Here, in this city, one could travel to one area and make a turn into another world.  There, they would find the fledgling beginnings of an expansion, sprawling from that central point.



It was too much to manage.  Even the smallest villains had elbow room to maneuver and manipulate.



``I've never been one to couch my words.  I'm direct, like my lasers,'' Legend said.  ``It's beautiful and it's frankly terrifying.  The Endbringers are, we're praying, dormant.  The major players are busy recovering and rebuilding, giving us six straight months of \emph{peace} for the first time in twenty years.  If you count non-parahuman conflict on a global scale, well, I don't know how long it's been.  It's been a hell of a while, if ever.''



Ciara closed her eyes briefly.  When she reopened them, Legend was his human self.



Tiring, to maintain focus.



``The peace will end.  It always ends.  When things go bad, it'll be worse because we've had the break, because it's had time to \emph{stew}, and because we're still reeling from last time.  But I know you, I've fought alongside a number of you.  The badges you wear are signs of that.''



Ciara glanced around.  Like her, many of the capes wore a simple symbol on their upper arms, a golden circle with a golden dot in the middle.  For some, it was a loop of cloth, for others, it was engraved on armor.



A simple symbol testifying that they'd \emph{been there}.



``There's no more oversight, for better or for worse.  That means it's our job to keep our eyes open, to watch each other's backs, and to watch each other.  I can tell you right now it's not going to be perfect.  Maybe I'm a living reminder of the fact that we can't trust anyone.  For those of you who were paying attention, the circumstances of Alexandria's demise in Brockton Bay are a testament to what happens when the corruption runs too deep.  Nobody benefits.''



Legend sighed.  ``Some are still angry at me.  At Alexandria, Eidolon, and others, who played parts.  But you haven't spoken up, you haven't interrupted me.  I'd like to think it's because we're all recognizing the same fact.  This?  It's our second chance.  Something we've all dreamed about from time to time.  A chance to cut out the rot and start anew, to fix things that were broken before.''



There were one or two nods around the group.''And it's going to be \emph{hard},'' Legend said.  ``Those who know how badly we fucked it up on the last try, who know the full story, they get why this is so frightening a prospect.  We still have to clean up the messes from last time, and we have to be doubly, \emph{triply} sure we move ahead properly this time.  Already, there are people plotting to take advantage of present circumstances.  Already, there are things going wrong.  It's an uphill battle.''



``But,'' Chevalier cut in, ``Like those badges we wear show, we've all fought in at least one \emph{bitch} of a battle, and we came out ahead.''



``I'll be damned if we're not ready for this one,'' Legend agreed.



Cheers rose from the group.  Fists pumped in the air, boots stomped.



``And,'' Legend said, while the cheering was present but dying down, ``With all that said, we're moving forward with our second chances.  I'd like to introduce you to the newest member of our Wardens.  Valkyrie.''



He gestured, and the crowd parted.  All eyes fell on her.  When she stepped forward, she had to be careful, her longer legs unfamiliar.  Staying young had come with benefits.  The Crone, \emph{Schwarze Tante}, had been able to give Ciara some of the time she'd stored away.  The ghost of a hero called Thane had fashioned her armor, shield and sickle.



The crowd parted as she approached.



The body of a nineteen year old was an unfamiliar one, the costume even more so.  Gold and sky blue.  The cloth that dangled from her belt traced the insides of her thighs to her knees, the skirt stopped mid-thigh, silent even with the gold chains that traced its edges.  The mask didn't block any of her vision, but it pressed against her cheekbones and forehead, reminding her of its presence.  Even her hair was longer, tied back in a thick braid.



She liked the wings, though.  The wings were good.  The rest would take getting used to, after thirty years as the childlike Faerie Queen, but the wings were a natural fit from the start.



``You've formed a new Triumvirate,'' a cape in the crowd said.



It might have sounded accusatory.



``Valkyrie will be starting on the bottom,'' Legend said.  ``She'll earn her way to whatever rank is most fitting.''



There were murmurs in the crowd.  For many, the sentiment was the same.  \emph{I think we know what rank that will be}.



For every two people that thought the strength she brought to the table was a good thing, there was one who was suspicious, doubting, or discouraged. They knew who she was.  The figures that accompanied her made it clear enough.  She couldn't think of them as shadows anymore.



She liked debating \emph{words}, the power of words, of titles.  It had been her favorite part of the sessions with the therapist.  The subject of renaming them had come up in the recent past, along with the discussion of what her new identity meant, and her new name.



Valkyrie, warrior women who guided the souls of dead warriors to the afterlife.  These spirits were her warriors, not mere shadows.



No, perhaps two people in her camp to one person against was optimistic.  There were others harboring doubts, a little slower to offer their congratulations.  Given time and a night to think about it, they would start to think about what her presence meant, that they might fall in battle and that she would claim them for herself, adding to her own power.



Her vision flashed.  For a moment, she might as well have been in hell.  The capes here on the rooftop were inhuman, even monstrous, distorted and exaggerated.  The city glowed with the distant presence of other capes, as though it were on fire.



Valkyrie resisted the urge to pinch the bridge of her nose or shake her head.  Her heart pounded long after the image had faded.



Nobody had said this would be easy.  Just the opposite.



The speech was done, and the city around them demanded attention.  Slowly, capes began peeling away from the group.



``Hey, Valkyrie?'' Miss Militia asked.



Valkyrie turned her head.



Miss Militia jerked one thumb in the direction of a man with a massive round shield and spear.  ``Want to join us for a meal?  We're leaving on patrol soon, so we were going to grab an early dinner.  You're welcome to come with.''



Valkyrie opened her mouth to speak, then thought twice about it.



She was still learning to talk \emph{normally}, to stop affecting the faerie noble's manner of speech.  She was getting lessons, and it wasn't perfect yet.  If she spoke, it would turn heads.



Except here, now, she almost missed the familiarity of it.  The power of her old voice.



``No obligation,'' Miss Militia said.  ``Honest.  I get it.''



Miss Militia had been the one to invite Ms. Yamada in, to connect them, and give her a chance.  She knew, perhaps better than Chevalier or Legend.



Valkyrie offered her a tight smile, then turned to leave.



When she walked down the hall, flanked by her three chosen warriors, her heels struck the floor.  There were Wardens in the hall, talking.



``Where's Defiant?''



``Complete radio silence.''



She was half again as tall as she had been, fit, glittering in armor, carrying a weapon and shield, and she felt more \emph{fragile }than she had in a long time.



Incomplete.



Her vision flickered again, like lightning before a crash of thunder.



As the Faerie Queen, she'd had a mission.  She'd been a part of something vast, a powerful engine that had reshaped whole civilizations, then erased worlds from the universe.



``We've got muscle now.  Might be we can make headway.  Retake the Eastern Queens portal.''



``Shh.''  Eyes turned towards her.  They talked about her like she was a secret.



Too many people.  She needed to talk to the therapist, but Ms. Yamada wasn't here.  She'd come at a moment's notice, with only one phone call, but it somehow felt like that would only compound the feeling of fragility.



\emph{I wanted to be more human}.



Never \emph{human}, per se.  Only \emph{more} human.  Parahuman, instead of inhuman.



She'd spent so much time in therapy, figuring out what Scion had been to her, coming to terms with the loss of the pillar he'd become in her psyche.



In trying to distance herself from him, had she set herself on the exact same path?



Seeing the flickers in the crowd wasn't helping.  She avoided them, making her way downstairs, into an adjoining structure.  Once upon a time, she'd used that other sight exclusively.  In this, in the here and now, she was warring with the keeper of the dead.  A part of why she felt incomplete, fragile.  They craved purpose.  It took a special kind of willpower to avoid using abilities altogether.  Some did, but they were rare.



Using her power meant killing, it meant being around the dead, immersing herself in the gravest kinds of conflict.



Would her experiment in humanity be so short lived?



She found an empty hallway and took it.  Things were under construction here, hidden behind plastic.  She ignored it, taking the paths that were available to her.



Finally, she came to a large room, a cafeteria, apparently, unfinished.  Only half of the tables were present, the kitchen unoccupied and unstocked.  The serving area had two tracks where trays could slide.  One of the two racks was behind a thick plexiglass barrier.



She sat down on a table, her feet on the bench, lost in thought.



Not five seconds in, her official phone rang.



She ignored it.  \emph{I only want some peace}.



This wasn't \emph{her}.  Had it been madness?  Arrogance?  Joining the side of the angels?



Her vision was distorting.  Even this far away from other parahumans, her other sight was showing their presence as a glow, as ripples.  She turned her eyes skyward, but one figure streaked through the sky, well above her.



She heard voices, and turned.



``We meet again, Faerie Queen,'' the voice echoed through the chamber.



She turned to see a thin man accompanied by a brutish caveman of a figure, walking on the other side of the thick plexiglass.  A child was on this side, petite, blonde, wearing a sweatshirt and jeans with pink sneakers.



Valkyrie felt a pang of jealousy.  She missed her old body, and the girl resembled her, superficially.



``Goblin King,'' Valkyrie responded. ``I don't go by that name anymore.''



``A pity, a pity.  This is my Alice, visiting our not-so-wondrous Wonderland.''



``Riley,'' the girl said.  ``I keep telling you, it's not Alice, \emph{Riley}.''



``A mere title, not a name,'' the man tittered some.  It was an eerie sound, coming from someone his age and gender.  Not that Valkyrie minded.  She'd dealt with worse in the Birdcage.



``Nevermind,'' Riley said.  ``Alice it is.  Whatev.''



Valkyrie looked between the two.  ``Are you allowed to be here?''



``I'm incarcerated,'' the Goblin King said.  ``She's visiting.''



``Officially visiting.  They're watching me.  Probably watching you, too.  We've played nice for the last stretch, and the illustrious Nilbog gets visits as a reward, so long as he's good.  We each keep our distance from the barrier, and they don't use the cameras to fill us full of darts.''



Valkyrie followed the girl's eye to a camera mounted in the corner.



``As you can tell, I keep friends of the \emph{highest} caliber,'' Riley said.



``Yes, yes,'' the man said, seeming very pleased with himself.  The sarcasm appeared to be lost on him.  ``A fallen king is still a king, yes?''



``If he can hold his head high, then he's more kingly than a man who relies on the crown and silks,'' Valkyrie said.



``Yes!  Yes!  Quite right!'' Nilbog agreed.



Riley was smiling, as if despite herself.



The phone was ringing again.  Valkyrie canceled the call.  She knew \emph{why} they were calling, now.  They were less than comfortable with this trio in one room together.



No matter.



``I came for my weekly dose of sanity, if you know what I mean,'' Riley said.  ``Spend enough time with \emph{them}, you need a break from it all.''



``I \emph{do} believe I know what you mean,'' Valkyrie said.  \emph{You mean just the opposite.  A weekly dose of madness}.  \emph{A return to the familiar.  }Both for comfort, and to serve as a reminder of how far they'd come.



Dangerous, perhaps.  She wondered if she'd share this with Ms. Yamada.



Probably.  People would pass on word.  They were all being tracked, no doubt.



But would she share what this \emph{meant} to her?  That she felt more secure than she had, leaving the rooftop meeting and speech?



``Shall we share stories of long ago?''  Nilbog asked.  ``Of our kingdoms, as they were?''



``We could,'' Valkyrie said.  ``Tragedies?  Comedies?''



``In \emph{my} stories,'' Riley said, ``The line between tragedy and comedy is awfully thin.''



``I suspect my stories are mostly tragedies,'' Valkyrie said.  ``Everyone worth talking about dies in the end.''



``Just the opposite for me,'' the Goblin King said.  He ran one hand along the cheek of the neanderthal figure beside him.  When he turned to face the barrier, he limped, and the brutish man helped him stay balanced.  ``My favorites persist, they keep coming back to start the adventure anew, a little different every time.  This is my helper.  They allow me him, only him.''



For a man talking about comedies, he looked sad.



\emph{The amnesty still hasn't gone through in entirety.  There are snarls, like this king without a crown or a kingdom.}



There were distant running footsteps, growing in volume as they drew closer, suggesting that capes were en route to intercept her.



Valkyrie glanced over her shoulder.



``I suspect this visit will be cut short.''



``\emph{Fuck},'' Riley said.  ``Not that the goblin king isn't awesome, but\ldots''



She trailed off.



``Maybe another time,'' Valkyrie said.  She raised her hands as the capes entered the room from the far corner.  She had to pick her words carefully, so she wouldn't sound strange.  ``I'm being good.''



``We'd like to play it safe,'' one of the capes said.  ``If you don't mind.''



``I understand.''



``Another day, Faerie Queen,'' Nilbog said.  He smiled, bowing a little.



Valkyrie returned the bow.  When she rose to her full height, she was smiling a little in turn.  It surprised her.



Flip sides of the same coin.



Rebirth.



The act was an idle one, like one might move a hand inside a pocket to double check there was nothing inside it.  She used her power.  Bringing one of her warriors through, on the other side of the barrier.



The neanderthal reacted.  Valkyrie's warrior didn't manifest in full, but it flowed through the neanderthal's body before rejecting the host.



Almost.  Close.



\emph{Shepherd of the dead}, Valkyrie thought, as she walked away.  The Goblin King was shushing his creation.



They were all parts of a whole.  The Chirurgeon, the Maker, the Keeper of the Dead.  It only made sense that there would be synergies between such abilities.



A way to bring her dead back, perhaps?



She could see them, in the dark recesses, waiting, loyal, obedient.  The ones she'd collected, some still mending from the great fight six months ago.



She felt better now.  Less incomplete.  Her other half was content with this line of thinking.



She just wasn't sure where she'd take it.





