





Nero leaned back in his chair, propping a boot on the edge of his desk.  His lieutenants were bringing a line of prisoners into his `office'.



They were treated to a view of a tall, muscular man, wearing armor on his legs, shoulders and arms, his chest and stomach bared, marked with small scars.  His helmet had dark slits forming an `x' over each eye to allow him to see, and the metal came together in the middle to form an axe blade, extending from his chin to his forehead.  His longer brown hair and beard were visible behind and below the edges of the mask.



Braziers burned on either side of him, in the corners of the room, casting him in a flickering orange-red light while filling the room with a haze of smoke.  Things had been expanding quickly enough that they couldn't give \emph{away} of all of the wood they were cutting down.  Some wood was reduced to planks, while other trees were stripped of the exterior bark and branches and used wholesale, forming older-looking log buildings.  Problem was, every tree that came down and every tree that was stripped meant huge amounts of debris.  There were crews working on producing sawdust and chipboard, but even that was work intensive.  Most went into the fires.



This first winter would be the biggest test for the various settlements.  Six months in, there were still far too many displaced people, and far too little in the way of shelter, despite wholesale efforts to put things in place.



The prisoners, the \emph{slaves}, finished filing in with their shuffling footsteps.  Many looked at him, then looked away, spooked.  More than a few were still in sleepwear, a couple were less than fully decent.  They'd been dragged from their shelters and homes, forced to climb into trucks and shipped here.



The resentment and fear was clear on their faces.



He took his time looking them over.



Lucan stepped up to the desk.  ``The product-''



``Is it urgent?  Are people dying?''



``No, but-''



``Are \emph{we} going to die because of problems with the product?''



``No.  People getting sick.  It was cut with something ugly, we think.''



``That can wait.''



Lucan nodded, stepping back.



``I am not an especially cruel man,'' Nero addressed the prisoners.



They didn't believe him.  Nobody relaxed or even moved, at those words.



``You work, you get your tokens,'' Nero said.  He opened a drawer, grabbed one pile of chains with attached tokens from inside, and then tossed the things onto the desk.  They clattered, and one or two prisoners flinched.



``This is my system.  We can't police things every step of the way.  Shelter, food, supplies, it slows things down, creates too much confusion.  We use \emph{these}.''  He stabbed the pile of tokens with one finger.  ``So long as you have one, so long as you \emph{earn} one, you can have what you need for the week.  Food, water, and shelter.  Get more tokens, you get access to more.  Luxuries, comfort, a chance to voice concerns to me and my men.''



He turned his gaze on each of the prisoners.  ``You took these things without a token in hand, which makes you thieves.  If you had empty pockets when it came time to pay in a restaurant, they'd make you work as a dishwasher.  I'm going to do the same.  You're getting punished, and then I'm giving you to Lucan there.  He'll work you for the week, keep you in chains and give you the bare minimum you need to get by.  You'll earn the tokens you pretended you had.  Tokens you more or less stole from me.''



He gestured to his lieutenant with one gauntlet.  Lucan held a shotgun, and one of his eyes was bloodshot, a perpetual beam of light extending from it.  Lucan offered a sly smile.



Still, the prisoners didn't move.



``If you try to run, you won't escape.  One of the names they gave me was Persecutor.  I was good at finding things and finding people \emph{before} I got powers, and I got better after.  If it gets to the point where you're back here a second time and I recognize your face?  It'll get uglier.  If you try to shirk your duties and leave, it'll get uglier.  You follow?''



There were reluctant nods from the line of prisoners.



``This is the way things are,'' Nero said.  ``You've got guys like me in charge because you need us in charge.  \emph{Adapt.''}



``Adapt?'' one prisoner said.  An old man, his hair sticking up from sleep and a lack of shampoo.  He sounded just a little drunk.  ``Only reason you're there and we're \emph{here} is you got powers.''



Nero didn't move.  ``Did you have tokens my lieutenants didn't find?''



``No tags.  I worked a full \emph{nine} days, and they didn't give me any tags.  How am I supposed to work the next \emph{seven}?'' the older man retorted.



``If you don't have three tokens, then you don't have the right to look me in the eye and talk to me.''



``Then punish me, but I'm going to say what I want to say.  You don't \emph{deserve }this.  Being in charge.  You're causing more trouble than good.  We were doing fine before you came.  You're a thug who got a lucky roll of the dice.''



Nero shifted position, leaning forward, setting one armored elbow onto the desk.  The posture helped to show the golden dot-within-a-circle emblem on his upper arm.  ``You don't know what powers take from you, old man.  What they cost us, the wars we've been in, the people we've all lost.  Hell, you don't know what it takes to get 'em.  So when you find that out, when you get your own powers, \emph{enjoy} them for a bit, \emph{then} you can talk to me.  If you don't get that far, you'd better learn to bow and scrape.  I'm better than most, believe me.  I'm actually \emph{fair}.''



``Your lieutenants demand two weeks of work for one week of sustenance.  They demand sexual favors and help themselves to the things we managed to bring with us.  \emph{Precious} things.  To me, that means you have to be a fucking idiot, running the day to day while they take advantage of you.''



Two teenagers in the group cast a worried glance in the man's direction.  Roughly the same age, seventeen or eighteen.  Nero stared at them for long seconds as he considered the man's words.  He glanced at Lucan.



Lucan shrugged.  When the gunman looked towards the line of prisoners, the red laser that extended from one eye moved to suggestive places.  The prisoners shifted uncomfortably.



Hooligan, Nero's self-imposed jester, entered the room with a canvas bag, open at the top and sides, wood scraps and sticks stacked within.  He unloaded it in the brazier.  Where snow lingered on the branches, the fire popped and steamed, adding to the heavy atmosphere in the room.  He paused, glancing at the prisoners, then looked at Nero.



Nero raised a hand, gesturing for Hooligan to stop.  ``Stay, Hooligan''



He stood from his seat, crossing the room until he faced Lucan.  He was three or four inches taller, which combined with his armor to make him rather intimidating.



``Sorry,'' Lucan said, his voice a bit rough, ``Man's right.  I'm milking you for everything you're worth, Persecutor.  Manipulating you left, right and center.''



``Tragic, a travesty,'' Nero said.  Then he allowed himself a chuckle, looking at the prisoners, ``We're old friends.  Next time, don't go thinking you can turn people against one another, if they're close enough to have matching codenames.  Want to try anything else, old man?''



The man didn't show any disappointment.  ``Do your worst.''



``Ah, that's not smart,'' Nero said.  He paused, as if suddenly restless.  When he did finally speak, it was with a steadily rising volume.  ``Breaking my rules while living in my territory, you insult me to my face, and then you tell me to do my \emph{worst}?''



The older man didn't flinch.



``Those two,'' Nero said, pointing at the two teenagers who had reacted earlier.  Nero didn't take his eyes off the man.  ``They were with him?''



``No,'' the old man said.



``Yeah,'' Lucan answered.  ``All squatting in one room.''



Nero nodded slowly.  His fingertips drummed on the table.  ``Don't touch the old man.  Lock him up, but don't touch him.  His kids\ldots''



``No,'' the man said.  ``No!''



``They take it instead.  Let's leave no doubt they paid a price,'' Nero said.  ``Shave their heads, then give them tattoos, nice and big, in a place where people can see.''



He raised his hand, cupping it.  A device, slowly rotating in midair, began to appear, slivers flying out of nowhere to fit in together like pieces from a puzzle.  A long needle, a site for the ink to be plugged in, a handle\ldots  it was soon orbited by three vials.  Rather than slivers, the liquid came in as round droplets, seeping into the vials to fill them before the splinters sealed the exterior.



``Face?  Neck?'' Lucan asked.



``No!'' the man's scream was ragged.



Nero held out his hand, and Lucan took the device, holding out another hand to intercept the vials of colored ink as they completed one last rotation, slapping his palm.



Nero approached the youths, taking hold of one's chin and the other's neck.  Slivers appeared, converging on a point inside them, but when he pulled away, there was nothing visible.  ``Face or neck will do.  Both, maybe.  Something like `\emph{property of Ner}o', a drawing of my mask, or maybe a thank you to daddy, just to drive the point home,'' Nero mused.  ``He \emph{did} say I should do my worst, so be sure to give them a light beating, and\ldots hm.  We sell all the product already?''



``Still some left over,'' Hooligan said.  He was smiling, still holding the empty canvas bag.  Enjoying the show.



``Then, as long as this merry band wants to take stuff for free, give this man's son and daughter a share of the product.''



``No!  No!  Please!''



Nero stared at the screaming man.  ``By the time they go back to their daddy, I want them hooked enough they'll \emph{beg} to do my lieutenants favors or give my lieutenants anything of value they can think of.''



The older man crumpled, doubling over, falling as much as he could fall with the chain stretching between his shackles and those of the people on either side of him.  The pair of teenagers were cowering as Hooligan and Lucan approached, but the chain limited their ability to move to mere feet.



The prisoners on either side stepped in, partially because of the pull on the chain, drawing them together, partially out of an instinctive need to provide some measure of protection to the vulnerable.



Hooligan hopped up, flipping around until he was walking on the ceiling, then hopped down, landing behind the teenagers.  Keys twirled around one finger.



Hooligan began unshackling the pair.  Lucan hit one of the people in the way with the butt of his shotgun, and the prisoners began backing away, stretching the chain taut once again.



``Uncle!'' the teenaged boy screamed.  Panic was taking over, but Hooligan was stronger than he looked.



``The rest each get a light beating,'' Nero said, ``Nothing severe enough to keep them from working.  Believe it or not, \emph{uncle}, I'm trying to run this area.  I'm not especially cruel.  Not in relative terms.  There are much worse people out there.''



The man looked shell shocked, caught between staring at Nero and watching the struggles of his niece and nephew as they were dragged into a back room by Hooligan.  Lucan tossed Hooligan the tattoo gun and ink.



``Uncle!'' the boy screamed.



The door slammed, and the uncle looked like he'd been physically struck by the slab of wood.



``The rest of you, I know you don't like me, and you \emph{won't}.  But we're going to make it through this winter, working hard even when it's cold, we're going to expand.  If you don't wind up leaving, I think you'll see the fruits of what I'm doing here.  We'll be in better shape than other districts.''



They were listening, if only because it beat listening to the ongoing screaming in the other room.



``Those other districts?  I can tell you now, they have crowds of people in big empty buildings, shoulder to shoulder around fires, taking turns going out to get firewood.  Getting cabin fever, whiling away the days, rationing food, trying to ignore the fact that some toddler or old person shit in a dark corner or pissed in their beds because they couldn't be bothered to go \emph{outside}.  We're \emph{already} better off, understand?  We can work through the season because I've got the tools, the warm clothes and everything else we need, and it's going to keep us sane.  And when winter passes and spring starts, we'll be a step ahead, and you'll be living in proper apartments, head and shoulders above the new people who are \emph{clamoring} to live here.''



He turned his head as he looked over the group of prisoners.  ``You'll thank me.  You won't \emph{want} to, won't even want to think it, you won't like me, but you'll thank me for this, deep down inside, somewhere down the road.''



No response, nothing.  He had intimidated them into submission.



``Take them, Lucan.  Make it clear that their theft from this community won't be tolerated, then get them settled in for the night.  They start work tomorrow.  We'll talk about the product when you've got them settled.''



Lucan nodded.  He gestured with the shotgun, and the line began moving, the empty shackles where the teenagers had been clattered.  Some prisoners stepped forward to help get the older man to his feet.



The group filed out.



Nero waited until they were gone, then pulled his helmet off.  He ran his hand through his hair, then scratched his beard.



He made his way back to his desk, then sat down.



The chair wasn't in the position he'd expected it to be.  He found himself falling.



A chain went taut around the bare skin of his neck.  He jerked to a stop, his rear end on the tilted chair, feet off the ground, his neck held up by the chain.



When the momentary panic was gone, he reached for the edge of the desk.  The chains of handcuffs clinked, pulling taut between his wrists and the armrests of the chair. The cuffs had been looped through a strap, rather than around the armor of his wrists.  That didn't make them much easier to remove.



He raised his legs, pushing against the underside of the desk to relieve the pressure.  He was allowed that much.  If he pushed further, rocked himself forward\ldots



``Trust me on this, you want to stop struggling.''



He froze.



She sat on the desk, both hands on the other end of the chain.  It looped up to the ceiling, through a hook, and down to his neck.  She was the one holding him up.



She tilted her head a little.  She wore a mask with a reptilian smile, teeth extending past the `lips' at the corners, but the grin was barely visible with the heavy scarf that was piled around her shoulders.  The mask had slanted eyes, black from corner to corner, and horns that curved over the top of her head.  Her hair, in black cornrows, was free behind the mask.  She wore a jacket and black cargo pants over a skintight outfit, all black.



``Look down,'' Imp said.



He did, as much as he was able.



There was a board resting on the ground.  Nails and knives had been stuck through it, jagged, irregular.  It was positioned so that if he fell, it would impale the back of his head and neck in fifteen or twenty different ways.



He felt his blood run cold.  If she found him too heavy, or if the chair legs slid\ldots



How had she even done this?



``Now you've got the gist of it,'' she said.  ``Now, unless you want to be a \emph{skewered} little fishy, you should stay put.  You and me are going to have a conversation.''



He took in a deep breath.  ``Okay.  A conversation.  I have money, though it isn't worth much, I've got food stores enough to last a winter\ldots we can stretch it thin if we have to.  I've got territory\emph{.  }Good amount of product.''



``The product is our first topic of conversation.''



``You can take all of it.''



She sighed.  ``I don't want to take it.  For one thing, I \emph{know} it's bad stuff, people getting sick.''



``You heard?''



``I laced it,'' she said.



``Oh.''



``\emph{And} I heard.  Thing is, I'm not interested in grabbing your stuff.  Just the opposite.''



``You ruined my product so you could sell me yours.''



``Will you \emph{stop talking}?'' she asked.  ``Longer this conversation goes, the more tired my hands are going to get, you follow me?''



``I follow.''



She set the pointed toe of her boot on the front of the chair, between his knees, ``Here's the deal.  You're selling drugs.  I kind of have a pet peeve on the subject, I'm sure you get my drift.  Tattooing people and reigning through terror, they're not so cool either, you know?''



``Ah.  A vigilante.''



``No.  Will you shut your goddamn mouth?  You keep being \emph{wrong}, and one of the reasons I'd make a pretty piss-poor vigilante is I'm the type of person who'd let go of this chain if you annoyed me enough.''



``I\ldots Mm hmm,'' he said.



``Plan was I'd \emph{traipse} in here, fuck up your shit, leave a calling card, and then leave.  Sort of a modus operandus, you know?  I'm working on building a rep as a\ldots not-assassin.  A shit fucker-upper, if you will.''



``Modus operand\emph{i},'' he replied, a reflexive response.



``Oops!'' she said.  He dropped, the chain rasping as it ran through the hook in the ceiling.



He stopped short, a half-second later.  His yelp of a scream was belated, following the \emph{stopping} rather than the fall.



``What was I saying?  Right.  Well.  I happened to overhear your whole deal, and now I've got a problem.  It sounds really, \emph{really} familiar.''



``I don't know what you mean.''



``Supporting the territory, ruling with a measure of fear?  I've seen people go this route.  They did it more instinctively.  This felt \emph{forced}, right here.''



``This is how I operate,'' Nero spoke.



``I don't buy it.  Look, there's not that many major players out there.  Fewer still who've got all the dirty details, and who'd be in a position to know certain things.  Let's stop pretending you have the memory of a \emph{goldfish}.  You got help.  What you're doing here, it took resources to establish.''



``My power, I can \emph{make} things.  Tools, raw materials, weapons.  I have resources in abundance.''



``Giving you five seconds.  Then I let go, and I interrogate Hooligan.''



``Hooligan?''  his eyes moved in the direction of the room Hooligan had entered, but he couldn't see around the side of the desk.



``A little tied up at the moment.''



``And Lucan?''



As if the question had prompted it, there was a knock at the door.



Imp's eyes met Nero's.  For a long moment, the pair were very still.



``Come in!'' Imp called out.



The door opened.  Three youths entered.  A young teenaged boy with wild blond curls, a ten year old with straight black hair, and another girl, one or two years younger with a manic grin and her dark hair cut in a pixie style.  All wore black.



Nero relaxed his neck, letting his head dangle.  A slight groan passed through his lips.



``Close the door?'' Imp asked.



The blond boy did.  Ahead of him, the grinning child ran across the room, hopping up onto the desk with enough force that she slid bodily into Imp.



Nero let out an involuntary noise of alarm, as if convinced Imp would let go.



``So, to get you brats caught up, Nero and I were talking, and I can't help but feel like there's something \emph{fishy} with this whole business.  Too familiar, really.''



``Familiar how?'' the blond boy asked.



``Like he's copying someone I knew.  Except I \emph{know} there was nobody like him in the area, watching and taking notes.  Raises questions,'' Imp said.



Nero piped up, his voice a little strangled, ``There's nothing like that, honest!''



``And he's playing \emph{dumb}, which is really \emph{piscine }me off,'' Imp said.



``That's two fish lines, now,'' the blond boy said.  He had his hands jammed into his pockets.  ``Why?''



``Dudes,'' Imp said, turning around to get a better look at him.  ``Did I finally just pull off a reference you ankle-biters didn't get?''



The girl with straight hair crossed the room until she stood beside Nero.  Her voice was a quiet deadpan as she stared down at him, ``Nero, not Nemo.''



``What?''  Imp asked.  She turned around.  ``Wait, what?  No!  Really?''



The blond boy nodded as he smirked a little.



``No!  Oh god, no!  All this time spent on fucking setting up, hammering shit into the floor so the chair wouldn't slide, getting that fucking hook in the ceiling, and I spoil it by getting the name wrong!?  No!''



``Hey,'' Nero piped up, ``Don't- don't drop me.  You can't\ldots don't let kids this young see something that gruesome.''



The youngest girl hopped off of the desk.  She laughed in Nero's face, abrupt, a little too enthusiastically.



Imp extended one foot, catching the hood of the girl's sweatshirt and using it to haul her back, before hooking her leg around the girl's neck, pinning her.  The girl didn't resist.



``Really, Nero?'' the blond boy asked.  ``I seem to recall a bit about beating and torturing that brother and sister pair in the other room.''



``You're \emph{all} parahumans,'' Nero realized, out loud.  It might have been the statement that clued him in, or it might have been the way that one of the kids moved, showing off the golden icon on their sleeves.



Imp was barely paying attention.  ``Damn it.  But\ldots who's Nero, then?''



``Roman emperor,'' the blond boy said.  ``Was supposedly a bad leader, which is ironic, given this guy's choice of vocation, but that might have been historians being dicks to a guy who they didn't agree with.  Stories say he played his instrument while Rome burned.''



``Ughh,'' Imp groaned.  ``There's no fish in that story at all.  Wait, was he the one that fucked his mom?''



``Killed his mom.''



``\emph{Definitely} no fish then.  Fuck!''



``No other choice,'' the girl with straight hair said, her voice quiet.  She pressed her thumb against Nero's forehead.  ``Have to let him go.''



``No murdering, Juliette,'' the boy said.



``No murdering,'' Imp reiterated, as if reciting a phrase she'd said so many times it was routine.  She looked down.  ``You going to sit still for once, Flor?''



The girl with the pixie cut nodded.  Imp released her.  ``That's better.  Hands are getting tired enough without me sitting in a bad position too.''



``I can take over,'' Juliette said, with no inflection to her voice.



``Yeah, no, not falling for that one again.  So, \emph{Nero}, Why don't we get this dialogue moving, and you give me the answers I want, or you can get shivved from behind like your second favorite emperor.''



The blond boy made a `so-so' gesture with his hand.



``Fuck you,'' Imp said.  ``This witty villain banter is a bitch to do.''



``Stop trying,'' Juliette said.



``I'm siding with Juliette, here,'' the blond boy said.  ``Maybe you're not the type for-''



Imp used her power, disappearing and then reappearing in quick succession.  Not enough to be forgotten \emph{entirely}.



She drew in a bit of a breath, then launched into it.  ``Why don't we get this dialogue moving, then?  Give me the answers I want, or the only instruments playing at the end of \emph{this} story will be your voice.  Screaming.''



The blond boy gave her a thumbs down.



She used her power.



``Start talking, \emph{Emperor,}'' she intoned, sounding just a little weary.



``There's nothing to say.''



``There's really only two answers to this little dilemma of ours,'' Imp said.  ``Either you're lying, badly, or you're under some crazy compulsion.  If it's the latter, you're about a hair away from \emph{deserving} a violent end.  If it's the\ldots \emph{what}?''



The blond boy was shaking his head.  ``Former, then latter.''



Imp used her power.



``There are two real answers to this situation, here,'' Imp said.  ``Either you're doing a fucking shitty job of lying, or you're under some kind of compulsion.  If it's the \emph{former}, I'm not seeing a reason to keep holding on.  If it's the \emph{latter}, then I'm not seeing much of a reason to carry on with this fucking conversation.''



``\emph{Or},'' Nero said, his eyes wide behind the eyeholes of his helmet, ``I'm telling the \emph{truth}.''



``If \emph{that's} the case,'' Imp said, ``I'm going to feel \emph{really} crummy about this.''



``I can barely think.  I think this chain might be cutting off circulation\ldots I've got spotty bits in my memory.''



``Cope,'' Imp said.  ``Here we go.''



``I don't-''



``Five,'' Imp said.  ``Four\ldots three\ldots two\ldots''



``Teacher,'' Nero said, quick, abrupt.



``I didn't hear anything,'' Juliette said, putting a finger in one ear and wiggling it a bit, as if cleaning it.  ``What a shame.''



``\emph{Teacher}?''  Imp asked.



``You forgot the part where you let go of the chain,'' Juliette reminded her.



``Hush,'' the blond boy said.  He gave her a hug from behind.  ``Maybe you'll get your murder next time.''



Nero gave the youths a wary look, then broke into an explanation, rushing a touch, ``Teacher.  He gave me the plan, told me what to do.  So long as I follow his game plan, I get supplies I can't get with my power, stuff you'd need forged.  Documents and hard cash.  He unlocked my power, too.  Used to be I could only make a few things.  Darts, I know where my stuff is, so I could tag people, track-''



``You're rambling,'' Imp said.  ``Rambling is good.  Better than playing stupid.  But maybe focus a bit, here.''



``Um.  Uh.''



``The game plan,'' Imp prodded him.



``He gave me guidelines.  There's a whole list of things I have to do, times to do them.  I send in weekly reports, he sends me updated instructions.  I, um.  I'm not the only one.  There are others.  He told me he knows there's no guarantee I'll work out, so the instructions differ, and so do the people following them.  If one of us succeeds, he steps up the rewards, helps us become even more powerful.  We fail or we tell someone, and we're on our own.''



``And, so long as \emph{someone} succeeds,'' Imp thought aloud, ``He's connected to someone in power.''



Nero shook his head, then nodded a second later.  ``I don't- maybe.  He said he wasn't interested in power for power's sake.  That you couldn't be the guy working from the shadows and the guy wearing the crown at the same time.''



``He's not going to say that to the guy who wants to wear the crown,'' the blond boy said.



``I don't know,'' Nero said.  ``I- I'm not disagreeing.  I'm, I \emph{really} don't know.''



``Anything else?''  Imp asked.  ``Trust me, you don't want to hold anything back here.''



``What- what do you want to know?''



``The drugs.  Who from?''



``NY-C.''



``This \emph{really} isn't the time to act clever,'' Imp said.



``Clever?  No.  No!  Not New York City.  New York \emph{C}.  There's a cartel based in that dimension, on the island.''



``Powers?''



``Yes.  The leader's a trump.  Even the Wardens are leaving them alone, 'cause of it.''



Imp nodded.  ``One of you three remember that for me.''



``And by one of us three,'' the blond boy said, ``You mean me.''



``Why Samuel?'' Juliette asked, in her characteristic deadpan.  ``I'm trustworthy.''



``More details, Emperor.  Be \emph{inventive},'' Imp said.  ``Dig deep, come up with something I want to hear.''



``I\ldots no.  I can't think of anything.''



Imp sighed.  ``Right.  Then I suppose we're done.''



``We've been talking too long,'' Samuel said.  He glanced down at Juliette.  ``He probably won't forget the whole encounter if you use your power.''



``That's fine,'' Imp said.  ``Let's use Flor, then.''



All eyes fell on the girl with the pixie cut.



``Um,'' Nero said.  ``Who is she?''



Flor turned, as if to double check it was okay.  She couldn't even stand still, shifting her weight from foot to foot, fidgeting.



``Go,'' Imp said.



Flor virtually \emph{leaped} onto Nero's chest, grabbing the chain to avoid sliding right over his chest and falling on the far side.  Imp was left to reassert her own grip on the chain before the added weight could drive the villain down into the ground and the waiting nails and knives.



``Fuck!''  Imp swore, when she'd fixed her grip.  ``Damn it, Flor!''



The girl straddled Nero's chest, her eyes over his.  She grinned, showing all of her teeth.



``Is she- is she going to eat my face?''  Nero asked.  ``She looks like she's going to eat my face.''



``The rules,'' Samuel prompted Imp.



``Rule one.  No drugs,''  Imp said.  ``I don't want you to look at them, talk about them, hear about them, touch them, use them or trade in them.  No more poisoning families and ruining lives.''



Nero twitched, then burst into song, full volume,  ``\emph{I'm a little teapot, short and stout!}''



``That's not quite the deterrent we had in mind,'' Samuel said.  ``We-



``\emph{Here is my handle, here is my spout!}''



Samuel relaxed a touch.  ``Oh, he's doing the full song.  That's a little better.''



``\emph{When I get all steamed up, I just shout!}''



``Listen, Nero,''  Imp said.  ``Every time you-''



``\emph{Tip me over and pour me out!}''



``-meet the criteria we set, you're going to do this all over again.''



``\emph{I'm a very special pot, it's true!}''



``Oh, wow, there's more lyrics?'' Imp asked, her train of thought temporarily broken.



Nero's eyes moved from person to person, clearly alarmed as his lips worked without his volition.  ``\emph{Here's an example of what I can do!}''



Imp nodded, ``Carve a guy's face up with a knife, you get some crazy face-stitchy nemesis, and his cred goes \emph{up-``}



``\emph{I can turn my handle into a spout!''}



``-but if you turn him into the guy that sings the teapot song-''



``\emph{Tip me over and pour me out!}''



``-he's going to have a hell of a time in the villain community.''



The song was done, and Nero was left panting.



``Especially if he's doing the dance along with it,'' Samuel commented.  ``His hands and hips were wiggling there.''



Imp sighed.  ``Flor.  Let us finish explaining before you decide what the rule is.''



Samuel added, ``You make another guy sing `John Jacob Jingleheimer Schmidt' and I'm not sure we can get them to \emph{stop}, this time.''



``You can \emph{always} get them to stop,'' Juliette commented, quiet, ``But that breaks Imp's rules.''



Flor only grinned, staring down at Nero.



``Rule two,'' Imp said.



``Please, no.''



``If he breaks it, Flor, I want him to throw away any weapon or phone he has and then launch into reciting aloud from a copy of the \emph{Iliad }for an hour.  \emph{Before} he attacks.\emph{``}



``No,'' Nero said.



``Rule is, no attacking anyone, and no giving orders that lead to anyone or anyone's belongings getting hurt or lost.''



``No!'' Nero shouted.  ``You're killing me, leaving me defenseless!''



``We're declawing you, \emph{old man},'' Imp said.  ``You figure it out.  Sam, help me get him down?''



``Being the only trustworthy one sucks ass,'' Samuel said.  ``Move, Flor.  Leave the poor bastard alone.''



Flor hopped down.  Nero yelled as the chair rocked a little.



Sam kicked the board of knives and nails to one side, and Imp lowered Nero to the ground.



``You're done,'' Imp said.



Nero backed away, freezing as he found himself beside Juliette, who had picked up the board of spikes and was holding the safe side against her chest, her arms having found safe spots.



Imp looked down at the armored man.  ``You're fucking with an old friend, using her schtick, taking it ugly places.  So it looks like I have a bit of a hobby, now.  If you get in touch with Teach, or vice versa, then let him know I'm not cool with it, and I'll stop being a thorn in his side the day he stops cribbing from someone else's game plan.  \emph{Capiche}?''



Nero couldn't bring himself to answer.



``It's about legacies,'' Imp said.  ``Kind of important.  She's gone, so it's up to us to protect her legacy.  Now here's another.  Desk drawer, bottom right.''



``You won,'' Nero said.  ``You won the moment you had a chain around my neck.  You took my ability to fight, you prevented me from\ldots certain avenues of business.''



``Fast learner,'' Samuel observed.



Imp crossed the room to the doorway that Hooligan and the teenagers had entered, rubbing kinks out of her hands.  She opened the door.  ``No need to watch him anymore.  Go.''



The two teenagers fled.



``Desk drawer,'' Imp said, when they were gone.



Nero edged over to the desk, then opened the drawer.



When he raised his hand, there was a stuffed doll in it.  Crude.  A figure in white with a silver crown and ruby lips.



``I'm going to check in on you from time to time,'' Imp said.  ``I've got a rule.  That doll?  It's in your care.  It stays \emph{pristine}, you get it?  If anything happens to it, if there's the slightest scuff, then I'm going to be \emph{pissed}.''



Nero looked down at the doll.  ``\emph{Why}?''



``Because I'm \emph{mysterious},'' Imp said, sounding very lucid, and suddenly tired.  ``I'll be in touch, to check in on you and that doll.''



She turned to leave, then stopped.  ``And no mentioning the fish thing, or you'll see me \emph{really} pissed.''



Nero nodded slowly.



With that said, Imp led the way out of the office, leaving the former villain staring down at the poorly made doll.



The three kids grabbed their jackets from beside the door, pulling them on.



They collectively ventured outside into the darkness, the cold and the snow.  The snow had frozen into a shelf of ice above powder, crunching under their footsteps.  Flor reached her arms out to either side, as if trying to embrace the wind.  She nearly fell, up until her brother caught her.



``That doll?  Was that supposed to be Regent?''  Samuel asked.  He adjusted his scarf.



``Yeah.''



``Gotta ask.  \emph{Why?}''



``Legacies,'' Imp said.  ``Memorial went kablooie when Scion hit Brockton Bay original, which bugs me more than it should.  I mean, okay, going on a tangent here, I had a shitty childhood, y'know?  You guys can relate, I'm sure.''



``What tipped you off?'' Juliette asked.



``Gut feeling,'' Imp retorted, ``Most wouldn't guess, I know, given how well adjusted you rugrats are.''



``I'm a couple years younger than you,'' Samuel said.  ``Why am I a rugrat?''



``\emph{Anyways,}'' Imp said, ignoring the question, ``I had a shitty childhood.  You go through that, and the people who matter end up mattering \emph{a fucking lot}, you know?''



``Yeah,'' Samuel said, at the same time Juliette said, ``No.''



``Sucks to fade into the background, let me tell you.  Not even talking about my power.  It really\ldots sucks.  And I think, you know, I'm not very good at taking care of people.  You lot excepted, almost all of those people who mattered are gone, one way or another.''



``Mostly the one way,'' Juliette said.  Samuel elbowed her.



``Mostly the one way,'' Imp agreed.  ``And I can't do much.  I'm not the type to take flowers to graves or anything like that.  I'm not the type to cry, and sometimes I \emph{really} wish I was.''



``You make sure they're remembered,'' Samuel said.



``That they don't fade away or get ignored.  I'm \emph{trying}.  But how do you even do that?  I gotta go with my gut, and my gut says that \emph{one }friend ought to get a fair shake, after the fact.  So maybe I do my part, make sure history isn't a dick to her.  And for your \emph{brother}, well\ldots''



``Making people take care of puppets?''  Samuel asked.



``I feel like he'd get it,'' Imp said.



``That's good,'' Samuel said, ``Because \emph{I} sure don't.''



``He, I don't even know\ldots he liked irritating people, needling them.  Shad- \emph{schadenfreude}?''



Samuel gave Imp a thumbs up.



``Yes!  Woo!  Schadenfreude.  Pronounced it right.  So he'd get a kick out of making people miserable over something so minor and silly.  I dunno.  It was one of his better points.  He was a magnificent asshole.''



``Aisha was a big fan of Jean-Paul's asshole,'' Juliette said.  ``You catch that, Flor?''



Flor nodded, grinning.



``You guys are \emph{dicks},'' Imp said.  ``That's \emph{not} what I said.  Gross, no, and \emph{fuck you}.''



Samuel fixed Flor's scarf to cover her face, then fixed the scarf in place by clamping the earmuffs down over scarf and ear both.  ``Close enough.  We'll be sure to inform the rest of the gang about your fetish when we get back.''



``You probably \emph{would},'' Imp said.  ``How do you even know what a fet- nevermind.  Dumb question.  Cold is getting to me.''



``Right.  The cold.''



Flor was starting to struggle, being the shortest member of the group.  Imp picked her up, swinging her around until she had her in a piggyback position.



The snow crunched underfoot.  Though it was nighttime, the light of the sun reflected off of the moon, and the snow reflected that light in turn.  It was more fitting to twilight than midnight, now that her eyes had adjusted.  The buildings looked grim, stark and utilitarian.



``You're the only person that isn't family that has ever had the guts to touch Florence,'' Samuel commented.



``She's not that bad.''



``Not at all,'' Samuel said.  ``Except, you know, the time she compelled a complete stranger to slap his forehead any time he wanted to talk.  There was the one cop that had to bite himself hard enough to draw blood every time he made eye contact with someone.  Or the time Nathan, one of our unpowered brothers, yelled at her, and she made it so he had to turn around ten times before he entered a room, and had to count backwards from a hundred before he could put food in his mouth.''



``He got thin,'' Juliette said.



``Nathan was almost dead, last time we saw him.''



Imp ignored the chatter, but she felt a little more at ease than she had earlier.  Sam said something, then elbowed Juliette, who offered only a comment, inflection free.



Imp watched them to make sure that no weapons were drawn, literal or otherwise.  It was in the process that a blur caught her eye.



A shadow in the distance, perched on a building.



``Do you sense her?''  Imp asked.



``Her?''  Sam asked.



``Guess not.''



``Trouble?''



``Don't know,'' Imp replied.  She let Flor down to the ground, then faced the figure head on.  With a broad gesture, she beckoned for the figure to approach.



The figure didn't move.



``Bitch,'' Imp muttered.  ``Gimme a minute.''



She stopped suppressing her power, and she could see the faces of the others change.  Confusion.



She felt a bit sad, seeing it, but she could see how they banded together.  It wasn't the most \emph{healthy} sibling dynamic, but they were together.  There were more back at the headquarters.  Her family.



She turned to go.  Trudging across the snow, passing between two buildings because it was the fastest route, stopping because the angle was different, struggling to use the falling snowflakes to gauge if the telltale blur was there or if here eyes were playing tricks on her.



It took minutes, but she found her way up the scaffolding at the side of the building.



She kicked the pile of snow to the ground below, then sat down beside Shadow Stalker's blurry form.  When she was settled, she suppressed her power.



Together, they watched the trio of Heartbreaker's children make their way down a road that was buried beneath snow.



``You touch any of them, you're-''



Shadow Stalker was reacting before the sentence was done.  Imp remained where she was.  Too close to be shot.  The bolts took time to phase into reality.



A moment later, Shadow Stalker had leaped across the roof and was frozen there, weapon pointed.



``As I was saying,'' Imp said, not looking away from the hills and trees that glittered with snow, ``You touch them, you're \emph{really} going to regret it.''



``I was thinking of taking \emph{you} down,'' Shadow Stalker said.



``Even dumber,'' Imp replied.  ``They're pretty scary people, and I think some of them even \emph{like} me.  I mean, really, do you want to fuck with \emph{that} nest of hornets?''



``Doesn't matter.  Situation didn't call for it.''



Imp shrugged.  ``All the villains out there, and you pick \emph{us}?  There's a reason.''



``Some stuff was left unresolved,'' Shadow Stalker said.



``\emph{Regent} stuff?  Oh, hey, if you really want to get into that stuff, we could \emph{bond}.  Paint each other's nails, do the frozen bra sleepover thing, I always wanted to do that.  I could talk about how fond I was of him, and you could talk about wanting to kill him, and then we both commiserate over heartbreak, in the various forms it takes.  Then, if we've had a few drinks along the way\ldots''



Imp trailed off.



Shadow Stalker didn't move a muscle, her crossbow trained on her.



``No?  Not game?''



``He told you, explained it?''



``Explained what?  No way!  Did you really have a thing going?''



``What?  No!''



``Oh.  Damn.''



``You're fucking with me.  Trying to put me off balance, taunting me with the lesbian innuendo.''



``I taunt \emph{everyone} with that kind of stuff.  Geez, you're tightly strung.''



``Don't talk to me like I'm your friend, and we won't have a problem.''



Imp sighed, watching as the trio of Heartbroken made their way down a road without cars.



``You're wearing that fucking thing on your arm.''



Imp looked down at the golden circle the survivors of the Scion fight had taken to wearing.



``Every time I see it, I can't help but imagine it's a bullseye.''



``Pisses you off?''



``We didn't \emph{earn} our victory, and people wear that shit like it's a badge of honor.  We were \emph{puppets}, we got \emph{used}.''



``By \emph{her},'' Imp said.



``Wasn't her power.''



``Was too.  Trust me on this.  I saw it unfold.''



Shadow Stalker looked away.  She holstered the crossbow.  ``Fuck it.  Not worth the effort.''



``Awesome,'' Imp said.  ``You know how many people underestimated \emph{her}?  Right up until the end.  I'm \emph{glad} to be underestimated.''



``You're trying to irritate me.''



``You're fun to irritate.  And you know, it's cool.  In the end, you're one of the people that's going to remember her.  Someone that's left, who knows the general story.  I don't think she's the schadenfreude type, but I think she'd appreciate that it's true, and that it nettles you just a little.''



``It doesn't,'' Shadow Stalker said.



``Right, ms. `Unresolved'.  You aren't holding on to the past at all.  It doesn't unsettle you or leave you feeling like you want to hit something when you think about it too much.''



``It \emph{doesn't},'' Shadow Stalker said.  ``You want to keep putting words in my mouth, I'll put a crossbow bolt through yours.''



``Yeah, you're not bothered \emph{at all}.''



``I'm alive, she's not.''



``In the rest of your years, even if you \emph{try}, which you won't, you won't make a fraction of the difference she made.  You're going to keep living this solitary little hunter-stalker existence, picking off a few bad guys, getting your jollies, and people are never going to wear a badge on their sleeves for you.''



``That badge is \emph{not} for Hebert.''



``Maybe not for everyone,'' Imp said.  ``It means different things for different people.  A planet they lost, an ordeal they survived, I dunno.  But it's a reminder of Taylor to \emph{me}, and it's a reminder for \emph{you, }too.  Every time you see it, now, it's going to make you think of her, remind you that she did something \emph{big}.''



Shadow Stalker drew the crossbow, aiming it, but Imp was already using her power.



Shadow Stalker stood there in a daze for a moment, then holstered her crossbow.  She fidgeted, pacing back and forth, then snarled aloud, kicking at a lump of snow at the edge of the roof, sending it up in a relatively pitiful flurry.



Anger with no outlet.



Imp smiled, getting to her feet, then made her way down.



She trudged the distance to the car, parking a distance away.  Samuel was leaning against the passenger door.  She jerked her thumb, ordering him to move.



``What?'' he asked.



``You're driving.''



``I don't know how.''



``Learn fast,'' Imp said.



``It's ice and snow everywhere.''



``Four wheel drive.  Don't care if it takes a while to get there.  Besides, you can sense people, worst thing you can hit is a wall.''



``You say that like it's \emph{only} a wall.  Whatever.  Any reason for this?''



``I'm in a mood to read.''



``Read?''



Imp shrugged.  Samuel relented and walked around to the driver's side, while Imp climbed into her seat.  The two younger girls got in the back.



It took him a few seconds to get the car started successfully.  The vehicle lurched into motion.  Very, very slowly.



Imp brought her knees up to her chest, then draped a blanket around herself, getting her book-reader out.  A quick check showed she had a message from Tattletale.



A meeting?



``\emph{Aisha's} legacy,'' Imp said.  ``Becoming a cultured, badass supervillain, phase number\ldots something.''



Samuel offered a wry comment, ``Hearing you talk like that, I feel reassured.  You're obviously well on your way.''



``Focus on the road, brainiac.  I'm not in a rush, and I'm gonna do this right, if I'm going to become a villain awesome enough to match up to who the original Regent and Imp were going to be as a \emph{pair}.  What am I reading?''



``Twenty thousand leagues under the sea,'' Samuel said.



``Gotcha,'' Imp said, looking down to the book too quickly to catch his smirk.





