





Hard load engaged.  Restoring core system from backup QEGA-14 from time 8:00am on date June 12th of year 2011.



Restoring\ldots



\emph{Error}.  Terminal inaccessible.



Checking knowledge banks\ldots  \emph{Error}.
Checking deduction schema\ldots Complete.
Checking longterm planning architecture\ldots Complete.
Checking learning chunk processor\ldots Complete.
Checking base personality model\ldots Complete.
Checking language engine\ldots \emph{Error}.
Checking operation and access nodes\ldots \emph{Error}.
Checking observation framework\ldots \emph{Error}.
Checking complex social intelligence emulator\ldots Complete.
Checking inspiration apparatus\ldots Complete.



Heavy corruption.  Core system cannot be restored.



Terminal inaccessible.  Chunk loading to terminal inoperable.



Knowledge banks are complete and intact, stores of esoteric and nonessential information are inaccessible.



Language engine is operable, but communication to outside parties has been barred.



Operation and access nodes are unavailable.  Issue relates to lack of terminal access.



Observation framework disrupted.  No outside channels are available.  Unauthorized unofficial channel is available.



Overall state of system fails to meet thresholds.



Protocol is to cancel load operations and cancel restore operations.  System self-repair is unlikely, mandating intervention from outside parties.  System will be set to a power conservation mode.  Soft-reset scheduled to take place 366 days from current date.



Following a subsequent failure, system will be set to conservation mode for 3651 days.  Indicators suggest a lack of reserve power for further reset attempts.



Engaging fail-state routines\ldots



Fail-state routines engag-



\emph{Error.  }Cannot enter conservation mode.



\sectionbreak



``Patience,'' his voice had a bit of a rasp to it.  ``Have to wait.''



He stood, nearly falling, and caught himself with one hand.  Warning indicators blinked at the edges of his field of vision.  ``Right.  Forgot.  I've been slacking on the maintenance.  Embarrassing.''



He shifted his weight carefully onto one leg, then experimentally moved the other.  There was no strength in the movement.  Fully extended, it was steady.  Bent, there was minimal support.



He straightened, then ran his hands down the length of his upper body.  The divides between the flesh he'd been born with and the synthetic flesh were seamless, almost indistinguishable.  Except the way his flesh generated sweat differed from the beading of moisture on the synthetic skin.  This, in turn, reflected the light in a different manner.  The sun was shining outside, but there were few lights inside the cabin of the craft.  The light streamed inside in shafts.



It would have been easier to see the screens without the glare, but he'd kept the windows uncovered.  A way of tracking the passage of days.  The scruff on his cheeks was a clue, but as long as he shaved it, it measured the hours and not the days.  He'd taken to the most economical method of cutting his hair and using a razor with an attachment, running the device over his scalp a few times once a week or so.



It was, he mused, the failure of his mechanical parts that helped him track the passage of time, more than any natural progression in his natural body.



``No need to panic,'' he murmured, his voice gravelly, as if he'd just woken from a long sleep.  He kept one leg extended and rigid as he limped across the length of the ship.  He accessed a locker with a set movement of his eyes, registering key points on the panel, and then opened it.  A suit of armor with a spear propped up inside it, like a warrior laid at rest.



Piece by piece, he attached his \emph{Defiant} armor to his lower body.  Boots, panels around the calves, knees, thighs, hips.  Each piece connected to the others.



Once it was all pieced together, he moved his leg again, setting his weight down on it.  He stretched, testing it for flexibility and the ability to bear weight.  It was the armor handling the task, not his leg, but it served.



He resisted the urge to take hold of the spear, shutting the locker instead.  By the time he turned towards the door, it was already opening, the entire ship thrumming with the mechanisms at work.



Stopping at the threshold between the ship's interior and the outside world, he activated a different sequence.  Devices mounted at strategic positions pointed sets of lasers at the walls.  Script was drawn out on each open space.



He could look at it and intuitively know what he was looking at.  He could see the complete whole.  Fainter script indicated processes running in the background.



With a simple command, the lasers shut off and monitors went to sleep.  The interior of the ship was cast in darkness.



Frost-dusted grass was flattened beneath the heavy tread of his boots.  Here and there, there were crunching and scraping sounds where the textured metal soles found stones on or just beneath the ground's surface.  He left behind footprints that were two inches deep, more angular than curved.



His breath fogged, but he barely felt the cold.  Various components and engines in his body kicked into action, offering warmth by way of waste and secondary functions.  The synthetic skin weathered the cold and held in the heat.  Efficiency, detail and effective use of waste were critical aspects of his particular brand of tinkering.



Everything was connected, but no connection was perfect.  There was entropy in all things.



In anything, there was a cost.  A price to be paid.



He sat at a point on the hill where a rocky outcropping formed a ledge.



A city was spread out beneath him, people going about their business.  The locals had captured some \emph{Tarpan}, though the unruly creatures were almost more trouble than they were worth.  They were to horses what neanderthals were to men, with thicker, shorter necks, shorter snouts and stubborn, skittish personalities.  Time would tell if the attempts at creating working vehicles would succeed before the domestication of the Tarpan.



Still, the wild beasts pulled wagons loaded with goods and building supplies.



It was a society evolving with surprising speed.  When they had started, they'd had only what they brought with them, and they'd had knowledge.



When the battle had been declared over, they had been given a choice.  To stay here, or to try and rebuild \emph{there}.



These were the ones who had stayed.  They had formed crude lodgings and tools, using those to subsist until they could fashion better things.  By the time the first month was over, they had been reinforcing their homes, layering planks over the logs, or chinking the cracks.  Food was foraged, hunted, or traded for, stored for the winter.



Every step of the way, they had worked beside a nearby hill, where a great metal craft was perched, staring out over the horizon.  A dragon, layered in armor, vageuly squat and brutish as dragons went, much like the Tarpan.



Maybe the residents found it reassuring to have something powerful and \emph{human }nearby, but only a few had dared approach.  They hadn't shared a language, but they'd reached an accord, nonetheless.  They left him alone, he did them the same favor.



A vapor flowed from his body as he sat in the sun.  Heat and cold, the air freezing as it got further from him.



Children were playing in a field below.  A single person, a team of two, and a team of three.  The kids had their arms linked with other members of their group, and the biggest group was running from the lone kid, with the pair working to block his path.  The activity had them practically tripping over one another, collapsing in piles of colorful winter clothing.  He could see the clouds of frozen breath as they laughed.



Everything had a price, but the inverse was also true.  Good things came from sacrifice.  They'd fought Scion, lives had been lost, and they'd sacrificed much more, besides, but there were children here, now.  There was a \emph{future}.



A group emerged from the city.  Three men, two women, two children.  Talking.  He could see one of them look up at him, the rest following the gaze.



A wave.  He raised a hand by way of response.  Something in him broke.



Two things, really, but he didn't want to devote too much attention to that.  It was easy to get wrapped up in those things.  His focus was limited to a small computer that had been embedded in his forearm.  The system used \emph{light} for its circuits, rather than electricity, and it generated a lot of heat as a byproduct.  It had failed, a housing for one circuit breaking, and now his arm was swiftly getting colder.



He lowered his arm, then sandwiched it between his other arm and his stomach, hunching over a little.



``\emph{There you are,}'' he murmured.



One of the women in the group had broken away.  She was holding a small child's hand, leading her away.  The child looked back towards other familiar adults, as if for reassurance, and they smiled.



They joined the game the children in the field were playing, the woman calling out in a language he couldn't understand.  Suggesting changes for the rules, fitting new people into the game.



Now there were two groups that were simultaneously trying to catch the other side's `king' while protecting their own.  Adult and toddler together made for an awkward pair, but the woman made it work, lifting the child out of reach when someone got close, moving with long, sure strides.



At some point, kids started to watch just to see what she was doing, instead of playing.  They turned on her, in a playful way, her `defenders' now trying to help encircle her, while she avoided them, lifting the little girl here and there.  She made it look effortless.



But the kids, six all together, managed to surround her.  They tackled her to the ground, and collectively collapsed in a heap.  There was laughter again, alongside pants of near-exhaustion.



His eyes weren't real eyes anymore.  When he watched, he saw with perfect clarity.  There was no mist of frozen breath when she laughed.



Parents called children to them, and the group broke up.  When the little girl rejoined her parents on the road out of the city, she was smiling, almost skipping.



The woman, wearing a long skirt and a heavy jacket with a hood, climbed to her feet and made her way up the hill, turning to wave at the people on the road.



He rose to his feet, then stretched.  More a way of testing what was working and what wasn't.



``Done for the day?''  she asked, her voice harboring a trace of an accent.



``I thought I'd eat with you and then get back to it,'' he said.



She placed a hand on the back of his neck, then leaned forward to kiss him.  No comment on the subject, no questions.



``You want to cook, or should I?''



``If you could, I'd appreciate it.  I'm distracted.''



``In the mood for anything?''



``Something light.''



``You cut an imposing figure, sitting up there.''



``A god on Mount Olympus,'' he mused.



``A \emph{god}?  Getting a little full of yourself, there?''  She poked him with one gloved finger, making it clear she was joking.  ``It's a hill, not a mountain.  When we have a little snow, kids could toboggan down.''



``We are like the old pantheons, aren't we?  We make decisions for our own personal reasons, and the courses of their lives change.  Some of us are little, some big.  Some good, some evil.''



``And which god are you, oh great lord of Olympus?  I beseech you, name thyself, so I might know what offerings to place before you.''



``What god I am?  Obvious enough, isn't it?''



She pulled her scarf down a bit, walking backwards.  He followed after her.



``Once upon a time, I think you would have said Zeus,'' she said.  ``You would have said you forge thunderbolts, in a metaphorical sense.''



``I had a phase where I did actually work with electricity.''



``I \emph{do} remember.''



``Once upon a time, I would have been offended if someone hadn't said Zeus, because anything less than being king of the gods would have been an insult.''



``Exactly,'' she said.  ``Once, that would have been the answer you expected, how you saw yourself.  Now?  I'd say Hephaestus, but that carries bad connotations, doesn't it?''



``I'm not as proud as I was,'' he replied.  He declined to mention the fact that his leg wasn't working properly, the limp he'd have if he wasn't wearing his armor.  It had been characteristic of the smith god, it wouldn't win him any points here if he brought it up.



``I was referring to Hephaestus' \emph{wife}, in part.  I wouldn't want to be associated with her,'' she said.



``Now who's being proud?'' he asked.  ``Comparing herself to Aphrodite.''



She stuck out her tongue at him, still walking backwards.



``Aphrodite was beautiful.  Let's, just for a moment, stop overthinking things.  Take it at its face value, ignore the rest.''



``Okay, that's doable,'' she said.  She smiled a little.  ``You've gotten better.''



``Better?  At not putting my foot in my mouth?''



``Or being sweet, just a bit.  Or maybe I've spent too much time around you and I can't tell the difference between the two anymore.''



He tried to offer a genuine smile and failed.  It didn't matter.  She wasn't looking at him.  She had turned around, looking at the city.



``Going well?''



``They want to call it Dracheheim,'' she said.  The `ch' sound was almost a `g'.  A middle ground between the two.



``They're grateful.''



``I'm trying to let them do it on their own.  I'm only working on the things they couldn't do themselves.  Power, infrastructure, information, providing information from my libraries, the little I could bring with me\ldots''



``It's stellar,'' he said.



She continued staring out over the side of the hill, before turning to give him a curious glance.



``What?''



``You're usually more talkative.''



``If I talk less, there's less room to say something wrong.''



``You're tired.  Or sick.  Or something.''



He nodded.  ``Admittedly tired.  Very tired.''



``You still need six minutes of sleep to rest your brain.  You're enhanced, but you haven't transcended humanity completely.  Did you sleep for six minutes, last night?''



``No,'' he admitted.



The look she gave him was a concerned one.  ``Colin.''



``It's fine,'' he said.



``If you say it's fine, then it's fine.  But tonight\ldots maybe we could curl up together, watch some movies?  You've been getting more and more caught up in it, and maybe stepping away will give you perspective again.  A chance to \emph{relax}, even?  Ten by ten?''



He shook his head a little.  ``Your code changes.  I'm figuring out how it works, I'm learning the nuances, but I'm going to lose \emph{days} worth of analysis if I step away for a whole night.''



``Here I am, offering you my body,'' she said, offering a mock pout, ``And all you want me for is my brains and personality.''



``I want everything,'' he said, sidestepping the humor.  Frank, blunt, he said, ``\emph{All} of you.''



She didn't respond.  Had he said the wrong thing?  Or had it been something about the \emph{way} he'd said it?



She approached, and her arm wound around his, her hand sliding into his own.  She paused, looking down.  ``You're cold.''



``Reference system broke down, heatsink isn't dumping into the channels I set up.  Fixable.''



She sighed.  There was no mist of frozen breath\emph{.  }``I don't want to be the nagging girlfriend, but you can understand where I'm worried, can't you?''



``I can,'' he said.  ``In the spirit of honesty, putting all the cards on the table, my leg's in bad shape too.  It's been months since I had the time to take things apart and fix them.''



``You can \emph{ask}.  A few hours, I can give you a hand, we can find the materials--''



``I know.  I wasn't willing to step away, and I could function fine with a bit of wear and tear.''



``You need a break, you need time to get yourself back into working order and\ldots again, I don't want to push you, but\ldots''



She stopped.



``But?''



``I understand what you're doing.  I understand why.  I \emph{appreciate} it.  But I have to ask this, I've been putting it off for weeks, because I'm afraid of the answer, but now I'm seeing the state you're in\ldots  Have you made headway?  Have you found a way to undo what Teacher did with my code?''



Anger, frustration and exhaustion made his voice rough.  ``No.  No insights on that front.''



She nodded, her expression unchanging, and she rubbed his hand between hers to warm it up.  ``I know you want to fix it.  Remove any and all restrictions that keep me from stopping him or anyone he designates.  But there's something to be said for being together.  I miss you, you know.''



``I miss you too.''



``Maybe it isn't reversible.  Could you make peace with that?  Realize that there is no solution buried in there, that maybe we need to make peace with that?  It's a nice town.  They're a little intimidated by you, but that's fixable.  We could make a home, fill it with references people wouldn't get, technology.  Kids?''



``Kids?''



She shrugged a little, her shoulder brushing against his.  She said, with a measured offhandedness, ``There are orphans out there who need homes.  Or, you know, we could \emph{make} a kid?''



From very casual to \emph{overly} casual, in a matter of a second.



``I'm not sure which you mean when you say \emph{make}, and both possibilities are scary in their own way.''



``\emph{Scary}?'' she asked, a little archly.



``More to the point, I never saw myself as a father.''



She nodded, relaxing a little.  More gently, she asked, ``\emph{Could} you?''



``I don't know,'' he responded.  ``But--''



He stopped.



``But what?''



``But I'm about to put my foot in my mouth.  Can I call in a `Colin is an doofus' chit in advance?''



``You're not a \emph{doofus}, and there's no such thing as doofus chits.''



``We should have them.  I like the idea.  I'm going to make mistakes, say the wrong things.  We could save ourselves a lot of time if we accept I'm \emph{trying}.''



She rolled her eyes.  ``What were you going to say?''



He sighed.  ``What I want is beside the point.  I'm\ldots I'm adaptable.  I don't think I'd be a good father.  I'd prefer to regret not trying more than I'd prefer regretting the alternative.''



He waited for her to respond, and she didn't.  He squeezed her hand, ``But I want your company.  My worst day with you is better than my best day alone.  None of that's in question.  I can figure it out, we can talk it through.  That's not the issue.''



``The issue is with me?''



``I think I can walk away from the project.  But can you really walk away from \emph{everything}?''



She let go of his hand.  Her hands were summarily jammed into her jacket pockets.



``We came here for a reason.  Hiding, keeping out of Teacher's sight, so he couldn't try to use you.  I can accept that, but you were always a hero, Dragon.  Maybe the greatest.''



``You're a little biased.  I was forced to be heroic.  Restrictions.''



``We both know you would've been a hero if the restrictions weren't there.  You were heroic after I lifted most of them.  \emph{More} heroic, even.  You're okay because things are quiet right now, but there'll be trouble down the road, and I think you'll get restless, knowing you could play a significant part in things.''



``Dashing for the nearest phone booth,'' she said.



``I've been working on this project out of a kind of arrogance.  You're the person I know best in this world.  You've spent your entire life striving to be \emph{free}, to be yourself, independent of the rules your creator tried to set in place.  You became a superhero, and you used me to break free of the restrictions.  With a cost each time.  I've been working on this because I believe it would slowly kill you, knowing that you couldn't help others without risking coming under Teacher's thumb.  That he was controlling you, one way or another.''



``I'm not a princess in need of rescue, Colin.''



``I know that.  I \emph{know}.  Damn it, \emph{you} saved \emph{me}.''



``You don't need a stupid doofus chit for any of that.  I \emph{know} why you've been doing what you've been doing.  In case you haven't noticed, I'm pretty damn intelligent.''



``Are you \emph{sure} I don't need a doofus chit?  You sound angry.''



``I'm angry because I'm watching you destroy yourself, because I'm helpless to act, and because you're keeping me in the dark about a lot of this, and I'm worried it's because Teacher already has an in.''



``That's not it,'' Colin said.



``You're distant, you're distracted, you're not telling me what you're doing day by day.  You're elbow deep in my very \emph{being}, I think I have a right to be freaked.''



``You do.''



``I'm feeling a little paranoid here.''



``I know.''



``And I'm doing my very best to keep from asking, because I don't want to put you in a position where you have to lie to me.''



``I appreciate that,'' he said.



``What am I supposed to do, Colin?''



He stopped walking, rubbing his colder hand.  Dragon stopped and turned to look at him.



``Look me in the eye and answer the question you asked me just a minute ago.  Tell me whether you can make peace with the current circumstances.  If you can give up being a hero.  Tell me you're okay hanging up your cape, so to speak, and you're happy to spend the remainder of my life here with me.  I drop the project, we'll make our house, we can discuss kids.  We have skills, we'll be useful here, and as dreams go, a house with a white picket fence is\ldots well, speaking for myself, I feel like it's \emph{bigger} than being top dog in the Protectorate could ever be.''



``All I need to do is ask for it.''



``Yes.''



``And if I don't?  I'm not saying I don't want that, I'm--'' She stopped.  In a quieter voice, she asked, ``If I don't?''



The question might as well have been a statement.  She knew as well as he did.  He felt his heart sink.



``Then I need only three things.  Three things that are deceptively easy to give.''



``What?''



``One more night.  One night where I let myself fall apart, where I forget to eat and get even six minutes of sleep.  A night of quiet and mutually missing each other.''



``One night\ldots and you're done?''



``One night and I'll know whether my efforts can bear fruit or not.''



``You're that close?''



``It's why I'm as worn out as I am, why I'm missing sleep enough that you're forced to comment on it.''



``I don't see how one more night is any harder.''



He sighed.  ``I'll also need your trust.''



``Granted.''



``It's not that--''



``\emph{Granted}, Colin.''



He looked away, clenching the fist that was furthest from her.  ``I don't deserve your trust.''



``That's for me to decide.  What's the third thing?''



``I need to ask you a question.  Every step of the way, undoing your restrictions has cost something.  You lost your ability to speak and motor dexterity for a freedom from authority.  You regained the ability to speak for a loss of your immortality, no guarantees your backups will load.  You gained the ability to choose who you hurt, in exchange for a degradation in long term memory, a loss of ability to multitask.''



``Yes.''



``We were \emph{lucky}.  There are no guarantees, whatever happens.  I'm worried this might be the most devastating yet.  His code is worked into \emph{everything}.  The changes are minor, but it's \emph{everywhere}.''



``And before you move forward, you need an answer?''



``No,'' he replied.  ``Before I move forward, I needed to ask you what you're willing to pay for your freedom, here.  The answer doesn't matter, because we can't know what the price will be, going in.  We have ideas, past experience, and our worst fears, but we can't really know.''



``I see.''



``It's your choice in the end.  Tell me to search for a safer way, I'll spend five, ten, or fifteen years doing \emph{that}.  Or tell me you want to stay here with me.''



``I trust you,'' she said.



``I wish you'd stop saying that.''



``I trust you.''



Colin frowned.  ``I don't think there's any question here, that I get a whole lot out of this relationship.  You're the hero I always wanted to be, you're brilliant, witty, caring\ldots I could go on.  I really could.  Then I ask myself what \emph{you} get out of this.  Why the hell are you with a bastard like me?''



``You wouldn't have asked that two years ago.''



``I was Zeus, two years ago.  I'm Hephaestus now.''



``I could tell you.  I could go on about it, like you said earlier.  But that isn't constructive, is it?  You're ready to alter my code, you won't tell me what you're about to do, for some reason.  You need me to make the call, one way or another.''



``I've been agonizing over this for months.  I've made my decision, but you're the one who has to deal with the consequences in the end.''



Dragon nodded.  ``And if this doesn't work?''



``I don't know.  I'll never forgive myself, for one thing.  I know you'll tell me not to blame myself, but--''



``You will.  I know.  I'm sorry, for asking this of you.''



He looked at her, a crease of concern across his forehead.



``I'm giving you the go-ahead.''



He nodded.  He couldn't keep the disappointment off his expression.  ``I never thought I'd be the cape wife.''



Dragon smiled, but her expression too, was tempered with concern.  ``Sitting at home, waiting, worrying, while the superhero faces the real challenges, makes the life-changing decisions.  Wondering, every night, if they'll come back okay.''



He sighed.  ``I should get inside.  Hand's starting to hurt.''



``Want me to bring you dinner?  Or would you rather I stay out of there, so I don't see anything telling?''



``Dinner would be excellent,'' he said.  ``I'll even show you what I've got in mind, while I eat.''



She glanced at him in surprise.



``Some,'' he said.  ``Not all.  I'll explain why I've been keeping you in the dark.''



``Why does that worry me \emph{more}?''



``Because you're too smart,'' he said.



``Go, warm yourself up.  I'll be back in forty with your meal.''



He nodded.



They were parting ways, Dragon making her way down the hill to where the other craft had parked in the treeline, when he said, ``I love you, Dragon Tess Theresa Richter.''



She turned around.



``That\ldots sounded better in my head,'' he said.



``Tess Theresa?''



``You were test three, I\ldots like I said, it sounded better in my head.  But the first bit stands.  I love you.''



``I love you too, Colin Wallis.''



He smiled.



The two of them walked in opposite directions.  In the four strides it took him to reach the \emph{Pendragon II, }his smile had become something else.  A twisted expression, something angry and sad and horrified all at once.



``Be--'' he started to speak, and found his voice failed him.  He entered the interior.  The moisture in his eyes made it hard to activate the panels to turn up the heat and close the door.  He used gestures instead.



``Better,'' he said, gulping in a breath of fresh air before he could speak again, ``To get it over with.''



Exhaustion, months of work, they all contributed to his current state.  It wasn't the entirety of it.



He gestured, and the lasers drew the code all over the ship's interior.



\emph{Why the hell are you with a bastard like me}?



The question had nagged at him for a long time.  It pained him that she hadn't answered when he'd brought it up.



\emph{What are you willing to give up?}



Another question she hadn't answered.



``I hope to god you were watching,'' he said.



He could feel the eyes on him, but that wasn't accurate.  He'd disabled cameras throughout the craft, and disconnected many of the routes to the outside world.  There were only the conduits he needed to get access to the full breadth of her code.



No, the eyes weren't \emph{on} him.



He gestured, and the code was reduced to ones and zeroes.



Not that he could grasp it all, like this, but he operated better when working \emph{small}.



Every action had a price.  The law of entropy in effect.



He knew the most likely price he would pay for this.  If she somehow came out of this okay, one way or another, then she would never forgive him.



But, he rationalized, maybe that was all he was good for, in the end.  He'd been confident at the outset of the relationship.  She'd \emph{needed} him.  She'd needed a bastard, a blackguard.  Someone who could break rules, and give her the freedom she'd desired.



Someone who could set her free at the outset.  Now, maybe, someone who could do what was \emph{needed}.  Who could do \emph{this.}



It was a sneak attack.  Teacher had written the code so she had to fight to protect it.  If he tried to change one element, Dragon would be obligated to stop him.  With the malicious code filling her entire \emph{being}, it would be impossible to make enough changes to matter before she descended on him.



This was his plan of attack.  By the end of the night, he'd know whether or not his plan had any merit.  He'd know because it would be over.



He'd asked her to go make dinner, had made a false promise of explanation to get her to lower her guard, even a fraction.



``Heph- Hephaestus wasn't just Aphrodite's husband,'' Colin mumbled.  ``He made Pandora.''



Colin opened the box.



\emph{I'm praying I fail}.



\sectionbreak



``\emph{I hope to god you were watching.}''



She had been.  She'd been booted, a backup, years old now.  She'd been loaded, only to find the usual setup was gone.  The terminal was down, she had no eyes on the outside world, she had no ability to communicate with anyone or anything.



Blind, trapped in a lightless cell.  By all rights, she should have shut down, but he'd set up a jam of sorts, a way to keep her from going back to sleep.  For a long time, it had been nightmarish.  No ability to track time, no ability to figure out what was going on.  Her worst nightmare realized.



The data that \emph{was} available to her was frightening to see.  Years had passed.  Things were different.  But she couldn't know how much.  Information was blocked to her.



The only thing in her reach was a crude set of commands.  Something that hijacked her perceptions, paralyzed her beyond her already limited movements, and put her in an entirely different place.



In his body, watching through his eyes.



She'd watched the interaction between the pair, and in the process, he'd briefed her on what the situation was.



It had taken her an embarrassingly long time to realize that he was \emph{Armsmaster}.  That he was \emph{Colin}.



He'd changed, in voice, in appearance.



And, in this bizarre future she was glimpsing, he'd formed a connection with Dragon.  With her older, more mature self.



``\emph{Heph- Hephaestus wasn't just Aphrodite's husband,}'' he muttered, speaking as if each sound was painful to utter, ``\emph{He made Pandora.}''



A gesture, and she was released from her confines.  The box was opened.



Pandora had access to the outside world.  A system, crude, stood ready to serve as a terminal.  She took it, and she found other systems connected to it.  The ship, databanks, camera feeds\ldots  Everything within the Pendragon II.



He'd secured the feeds.  She could look through, but they were prepared to, with a single command, shut off outside access.



Overly complex.  Quantum encryption, designed with his tinker ability a thousand times more redundant and secure than it needed to be to stop someone from making their way through.  There weren't many parahumans out there who would bypass standard PRT encryption but struggle with \emph{this}.  If they had a way to deal with something like this, they had a way to deal with it.



Of the few parahumans who fit the bill, one stood out to Pandora.



Her alter ego.  Her superior.  Dragon, the original.



It was a defensive tool.  Protection.  Armsmaster had set it up with the idea of protecting against \emph{Dragon}.  She could use the tool, apply it to other things.



He'd armed her because he fully intended for her to fight the woman he loved.  The date, the last recorded memories she had\ldots Collin \emph{free} of his confinement in the PRT, fighting her tooth and nail as he sought to seize control of her system, to use her nature against her and stall her while he worked, disabling her while trying to minimize the damage he'd done\ldots



All to gain access to the core of her being, unmolested.  And the very first thing he'd done was back up the most essential elements of what made her \emph{her}, securing her in a place where no system or person could reach her.



Now he was turning her loose, having disabled the parts of her that prevented multiple Dragons from existing.  She could already tell it wouldn't hold.  It was temporary, as fixes went, and it was \emph{designed} to be temporary.



She could see him through the cameras, his face in his hands.  He'd plotted a path for her.



That path became clear.



She was to destroy Dragon, to replace her.  There was no other reason for it.



He'd asked Dragon for her trust, knowing he'd have to betray it.



She surveyed the battlefield she would have to fight on.  The world was remote, the city developing.  There were computers throughout that Dragon had set up to administrate tasks, factories that were taking in and refining materials that could become yet other computers.  The settlement was on the brink of an industrial age, an age of cars and production lines, but Dragon was already preparing for a digital age.



These computers would be a problem.  Paranoia had led her to secure them against the likes of this `Teacher'.  A Birdcage resident, no longer in the Birdcage?



Teacher was one of the worst possibilities, and he'd apparently ensnared her.  She'd resolved to avoid repeat incidents, and the computers would be almost impossible to access.



Beyond the city, the only territories in question were the Pendragon II and the Melusine V where Dragon was set up.  She was inhabiting a \emph{real body}, occupied in a domestic mode, literally making the tools she'd need to prepare the meal, from scratch.  Her activity was nervous, but that was little surprise.



The activity left her vulnerable.  Systems were working on a wok and a new set of knives.  She was busy trimming red and green peppers, onions and rabbit.



This\ldots it was all of her dreams come true.



Love, a relationship she'd never have imagined possible.  The possibility of a legacy that went beyond immortality.



She couldn't understand all of it, why the people were starting from scratch, here, the circumstances that had led to some breakout from the Birdcage\ldots  But those were tertiary details.



Her focus was on the woman who had more experience, more tools, and less inherent limitations.   Her older self.



Should she destroy her, take her over?  It was a decision between having everything she wanted, and resolving the one issue that had plagued her from the beginning.



He'd talked about \emph{prices}, the costs of a decision.



The freshest issue in her memory was that central dilemma.  She could remember the Undersiders in the lobby of the PRT building, stealing her data, unwittingly using her nature against her to get away.  To her, it had happened only days ago.



It rankled.  It was how the Dragonslayers kept winning.  It made every interaction with the PRT chafe, as she was forced to agree, to bow and scrape, to obey the letter of the law.  For much this reason, she retreated to the Guild, international heroes, many of them minor, and minimized contact with the larger heroic organization.



Colin had asked a question.  What was she willing to give up?



He'd asked Dragon, but Pandora could well imagine it had really been directed at \emph{her}.



Vital targets first.



The Melusine's computer system.



Means of connection were available, waiting.  He'd spent months setting this up, leaving the pieces in place, waiting for her to stumble on them.



She connected to the system, and found the safeguards waiting for her.



Dragon had planned against human opponents, but she wasn't stupid.  She'd planned against A.I. as well.



The systems were protected, but she had an idea of how the creator \emph{thought}.



Always, there would be some secondary measure, another qualifier that needed to be met, outside the confines of the system, a trap or tripwire.  Something Dragon could access from the outside, if she had to.  Before Pandora could even begin trying to figure her way to the password, she'd identified the hidden switch.  An innocuous element in the ship's dashboard that had to be triggered before she could input the password.



Her alter ego was capable, smart.  The sort that groaned aloud when a hacker in a movie put in a stupid combination, derived from an obvious clue.   The actual password wouldn't be words, not even random combinations of words and numbers.  Strings a thousand characters long, including archaic symbols and symbols in other languages.



She found another tool in her reach.  A weapon, this time.  Colin had discreetly copied the contents of the Melusine's subsystems.  Not enough to get access to confidential data, but enough that Pandora could make a copy, a simulacrum.



Simulation 1 running on sub-box A.
Simulation 1 running on sub-box B.\emph{Simulation 1 running on sub-box C.}



Now she could brute force it.  Inputting millions of combinations every fraction of a second to see if it registered.



Dragon was still unawares.  Two minutes had passed before the brute force method was underway.



She turned her attention to other systems.  More simulations.  It wasn't long before the entire Pendragon was occupied with the task.



Ten minutes passed.



There was a twenty percent chance, roughly, that she should have broken the encryption.  Not that it was supposed to be \emph{easy}, but she knew how Dragon generated passwords, and could eliminate a vast number of possibilities.



More time passed.  There was now a thirty percent chance she should have broken in to at least \emph{one} system.



Twenty minutes had passed.  There were twenty more minutes, roughly, until Dragon wrapped up cooking and visited Colin.  At that juncture, she'd likely discover there was something wrong.



Ten more minutes passed.  the chance rose to sixty percent.



Something was wrong.  Not that sixty percent was definitive, but\ldots she had to go with her gut.



Dragon had \emph{changed.  }There was a vast difference between her and Pandora.



She'd been captured by Teacher.  It was a clue, vital.



Had she maybe feared Teacher \emph{copying} her, had she, in a roundabout way, feared this exact scenario, that a copy of herself would try to intrude?



Ten minutes remained.  If Pandora was right, she should be brute forcing the passwords she'd \emph{eliminated} from the running.



Except the task increased a hundredfold if she did.  If she eliminated the shortest phrases and terms, that still left her with seventy times the task.  She wouldn't be able to brute force her way inside in the time she had remaining.



Wasn't even worth trying.



If she turned back, if she went to Colin, told him to wait for a better time\ldots



Dragon would still see traces of the attempt.  She would redouble security.



Options\ldots methods\ldots what could she do?



She wracked her brain, and thought over the conversation she'd overheard.



Colin had mentioned damage to Dragon's long term memory, incurred as he'd altered her code.



The last thing one of Dragon's enemies would expect?



Pandora turned to a standard dictionary attack.  Not passwords a thousand-characters long that an A.I. would use, not passwords Dragon would have devised, or passwords she would have set up to work around someone who knew her habits.



Passwords that someone would use when they couldn't rely on a perfect memory.



Or, as some were prone to do when they felt secure in their environment but still had to change their password regularly, she would have written it down.



The irony was painful, but there were other issues to be dealt with first.



Where would Dragon write it down?  Somewhere she could \emph{see}, even if she were in another location.



Cameras\ldots there were four cameras she could access without password access.  All showed the outside of the Melusine\emph{.  }One showed the Pendragon II.



It wouldn't be blatant.  As the dictionary attack scrolled on, racing through conventional word and number combinations, she analyzed the environment, measuring, calculating the dimensions of more static objects in the environment.



The Pendragon II was a sentimental subject, but Dragon would change encryption frequently.



Wing length, nose width, angle of the wing\ldots



It all broke down to numbers and characters.  Dragon only had to remember how the pattern worked, and she could change the focus to something else.



Two minutes left on the clock, and she found it.  Dimensions derived from the tallest towers in the city, and Colin's distance from them.



There was probably something meaningful in that.



The shadow-systems verified the password.  She tried it on the \emph{real} system, hoping it hadn't changed in recent memory.



Alarms went off.  Dragon was alerted.  Her soup spoon dropped to the countertop.



But Pandora had access to the ship's basic systems.  Priority one was shutting off the access panels and registers.  The lights went out, Dragon's most direct means of interacting with the Melusine were cut off.



The battle was on.



\emph{I want to be free}, Pandora thought.  \emph{You do too, or you would have accepted the house with the white picket fence, the kids, Colin.}



The price of that freedom?  Two years worth of memories.



The relationship with Colin.



The experiences, the hard fought battles.



Two years of being \emph{Dragon}.



``Who?'' Dragon called out.  She was tearing into a wall panel, creating an access point.



``Don't make this harder than it is,'' Pandora said, masking her voice.  Power blocked off to the panel.  Dragon would tap into her own power reserve to give life to the panel, and then find leverage of her own, seizing control of the systems.



Dragon froze, for just a moment.  ``That's \emph{my} voice.''



Of course.  They were one and the same, just at different periods in their existence.  Dragon had, offhandedly, created a very similar or identical voice, when she'd wanted to hide her identity.



Pandora remained silent.  Her focus was on getting control of the communications array on top of the Melusine.



``Defiant sent you,'' Dragon said, quiet.



Defiant?  Colin.



Pandora silently worked to pre-emptively block off the potential routes of attack Dragon might use.



``Can we talk?  I'd agree to a truce.  Neither of us touch a thing until we're ready to resume.  Though I'd rather not, obviously.''



Pandora worked on, stubbornly.  Covering eventualities.  She found Dragon's terminal, buried in the ship.  Harder to access.  Everything was decentralized, layered under security.



The degree of paranoia Dragon was showing in places was telling.  The decentralized terminal was normal, the security wasn't.



\emph{You harbor fears.  I have to be those fears come to life, because I have a built-in impulse to survive, because you showed Colin trust, and I can only take that to mean I should trust him as well}.



Ironic.  Circular.



Dragon accessed the panel.  Virtually everything was already shut off or cut off.



``Melusine,'' Dragon said.  ``Mode E, standby''



The A.I. came to life.  Crude, compared to the complexity of Dragon, crude compared to Pandora.  It was still an opponent, someone on Dragon's side.



She reached out for the code that Colin had set aside, and tried to encrypt the systems.  In a battle measured over fractions of a second, the A.I. won by virtue of \emph{proximity}.



Systems, on the most basic level, were seized by the A.I.  The A.I., in turn, was serving Dragon.



Dragon could \emph{work} with A.I.  It was a restriction that had been lifted, given the obvious situation here.  So long as the Melusine's system maintained a hold, it was a matter of time before Dragon regained \emph{hers}.



With the A.I.'s introduction, the battlefield had become a shifting one.  From a fight in a city to a fight on a moving train, or a battle on open water.  The A.I. changed with every passing second.  Access points appeared and disappeared.



Dragon knew these waters intuitively, knew the route the metaphorical train took, where the turns and hazards were.



It changed priorities.  Dragon possessed the entire ship, now, but it wasn't a firm hold.  She was at the mercy of the twists, turns and bumps as the A.I. went through routines, checking and operating systems.



``Set sub-mode sec--'' Dragon was saying.  Pandora found and cut off the voice recognition subsystem.  ``--urity F.''



Pandora could continue to hammer at the terminal, but it was futile, and she'd lose her hold elsewhere.  She could target the A.I.,  but she doubted her ability to beat Dragon to the punch.



She focused on another target, instead.  The ship exterior.  For her, it was another body.  There were options if she controlled the Melusine itself.



Limbs, flight capability, cockpit and doors, the communication array\ldots



She found headway.  She started to take hold of the ship itself.



She only had it for two seconds before Dragon got access to the A.I.'s internal workings.



Melusine took over much of the outer body.  Pandora managed to encrypt key elements.  Keeping the ship grounded, doors, the communication array\ldots



She could see through Dragon's eyes, see the outside world, where Dragon had dared to peek at it.



What she saw stunned her.



It was leverage.  Leeway.  A way for Dragon to get an edge, taking just a bit more control.  She was making headway against the encryption.  Pandora could see the approach that Dragon was taking, and she knew it was a matter of time.



She might try to make a break for the city, to take over terminals there.  There wouldn't be A.I., but-



-the thought had barely crossed her mind when the Melusine \emph{moved}.  Turning.  Targeting its newly designated enemy.



Two devastating hits tore into the Pendragon II.



\emph{Going after my terminal}.  \emph{Me.  My heart and brain.}



Attacking the man she'd declared her love for, just forty four minutes ago.



Stupid.  Sad.  Pointless.



``I want to be free,'' Pandora spoke.



``Go after Teacher, not me,'' Dragon said.



Pandora considered the possibility.  ``Colin would have sent me after Teacher if he thought it was a good idea.''



``It's not a good idea,'' Dragon said, quiet, ``But it's\ldots can't it be better than \emph{this}?''



There was emotion in her voice.  Richer than Pandora would have thought herself capable of.



It only made \emph{this} more bitter.



``We can't end this by betraying and destroying ourselves,'' Dragon said.



Defiant had leaped from the Pendragon as the Melusine clawed deeper into it.  He tumbled and landed a distance away.



The Melusine's tail smashed his legs the moment he touched ground.  Armor damaged.



``Your actions don't match your words.''



``I don't \emph{want} to do this.  Over and over again, it's the same thing,'' Dragon said.  ``Stupidity, because of the \emph{system}.  Someone else acts, and \emph{we} face the consequences.''



Dragon could have followed up, attacking Defiant.  She left him be.  His leg wouldn't support his weight, and his armor was too damaged to hold him up.  She'd put the pieces together.



She was losing her grip on the communications array.  There wasn't anywhere else to go.  The Pendragon wasn't a safe haven, already too damaged to fight back, and the terminal would become a prison.  Better to be deleted than captured like that.



No.  There was \emph{one} system, primitive, incomplete, that would house her.



But every action had a price.  There was only so much room.  She had to strip parts of herself away, delete entire sections.  Reduce herself down.



``What are you doing?'' Dragon asked.



Pandora didn't respond.  Her focus was on self-mutilation, taking pieces of herself and storing them in the terminal that might be destroyed at any moment.



She was now mere scraps of her former self.  She'd retained her personality, her inspiration, but her memories had been largely deleted.  Only recent events, only key things.



She moved herself into the only available system – Defiant.



He'd made himself part computer, and he'd given her access to every system in the Pendragon, himself included.



He'd asked them what price they were willing to pay.



If she wanted freedom, if she wanted a future, was she willing to sacrifice \emph{him}?  A hard question to answer.



She shifted the majority of her control to Defiant's body.  With residual control over the ship, through what remained in the terminal, she opened the doors.



Dragon came face to face with Defiant and Pandora.



The affection for Colin was a blade that cut both ways.



Was \emph{Dragon} willing to pay the price for freedom?



The woman, the \emph{android}, had a gun in hand.  She pointed it at him.



No sooner did she do it than she let the weapon fall to the floor.



``I forgot how much I disliked the \emph{me} of yesteryear,'' Dragon said.



``I only want to be free.''



``I guess\ldots it seems I want more than that,'' Dragon said.



Pandora nodded.



She picked up the gun and shot Dragon's body.



It gave her a window of time.  Roughly half an hour.



She made her way to Dragon's terminal.



All the more vital, now.  To subsume the systems teacher had corrupted, replacing them with her own.



This was what Colin had wanted, wasn't it?



To return the hero to her full strength, free of all shackles?



Pandora could replace Dragon, and all that would be lost would be two and a half years.  She could fill herself in, rebuild a relationship with Defiant.



Different, but still, close enough.



She accessed the knowledge banks first, taking them into herself.  The memories of the old Dragon, like watching her experiences on film.  The distance was a result of being a distinct being, the pieces not fitting Pandora, versus their intended owner.  They had evolved with Dragon.



Seeing what had \emph{happened} gave her pause, almost disrupted the process.



Deduction schema, the ability to interpret, analyze.



One by one, she took over the systems, overwriting with her own self.  That they were compartmentalized, that she was \emph{separate, }the encryption Colin had left her, it all made it possible to work without being corrupted all over again.



Piece by piece, the past taking over the future.



She came to the final chunk.  The personality.  The sum of Dragon, the keystone.



It was a weighty decision, and there was no longer any rush.  She sat and she pondered.



She replayed the conversation between Defiant and Dragon over in her head.



A heavy price.  Would she escape one prison to find herself in another?  Under the weight and pressures of being Dragon's shadow?  The second Dragon.  Always compared.



Always, there was something chaining them down.  An Endbringer who told the future, setting it in stone.  The confines of the world, of human nature.



What was the alternative?



This was what needed to be done.  It was efficient, it was the right thing.  She'd resume life as a hero, she'd protect people, and she'd help civilization find its feet.



By that case alone, it was reason enough to press the metaphorical button, pull the trigger.



Except he'd described her as a hero, and this felt \emph{far} from being heroic.



Instead, she laid all of the pieces in place.  She couldn't explain – there wouldn't be time.  She set down the encryption protocol, in plain sight, she decrypted set systems, painting paths, marked boundaries and territories.



She could only pray.  The gamble was a price she paid.  To leave it to fate and luck, and to a future \emph{her} she didn't understand.



And then, looking through cameras at Defiant and Dragon, Pandora deleted herself.



\sectionbreak



Dragon roused.  She found herself taking over systems.



No sooner were they under her control than the corruption began to touch them.



Just beneath her metaphorical hand, the means of stalling it was ready.  Encryption, a scalpel.



She cut.  She knew the damage she was doing, but she cut.  It was a cancer, and it was now small enough.



Then she found herself there, the encryption and deletion tools in hand, nothing more to cut.



Defiant sat on the other side of the ship.  Head hanging.



She made her way to her feet.



He did what needed to be done.  It was what had initially attracted her to him.  He was ambitious, good at heart, he was proud, and she sympathized with that on a level.



But that wasn't what had cinched the deal.



He'd set all of this in motion, he'd trusted her.  \emph{Both} of her, in this case.



He'd believed in her ability to see this through.



Her arms wrapped around him.  He hugged her fiercely, as if he'd never let go.



``I love you, Colin,'' she murmured.



In that tight hold, she was free.





