





The group made their way into the real city.  Buildings had gone up, and were now being added to.  Cranes were everywhere, the streets were filled with a strange mix of laborers and professionals, and it seemed like half of the vehicles on the road were carrying materials.



The crowd was more resilient than most tended to be.  The mutant wolf and its rider walked along the side of the road, and the people didn't cower.  They drew back, but there was no fear.  They faced the small group with shoulders squared, holding eye contact.  There was a kind of stoic pride that made them less willing to be pushed around, a unity that made the lawyers and businessmen fall in line with construction workers and cleanup crews.



The message was clear.  This was\emph{ their} territory.



\emph{Always was}, Rachel thought.  \emph{More their world than mine}.



``Damn,\emph{ civilization}!''  Biter commented.



``You think we can get any fast food here?''  Cassie asked.  ``A burger, pizza, um\ldots''



``Fried chicken,'' Biter said.  ``Hell, I'd go for just \emph{french fries}.''



``We don't have money,'' Rachel commented.



``We're villains,'' Biter said.  ``We could \emph{take} it.  Or cut out the middleman and go straight for the food.''



``It's a hassle,'' Rachel said.  ``I'd rather have a steak, some veg, and a good hunk of bread to soak up the juices.  That bread the other night was good.''



``Yeah?''  Cassie asked.  She smiled wide.  ``You liked that?''



``Didn't I say that?''



``You're telling me you'd turn down pizza?''  Biter asked, with a hint of incredulity.  ``You'd turn down a nice shawarma?''



Rachel shrugged.  ``All food is pretty much fast food when someone else does the cooking.''



``You're spoiling her,'' Biter told Cassie.



Cassie smirked, scratching the ear of the dog that walked to her left.



Bastard sniffed as they had to walk around an area where an overhang had been erected to protect people on the sidewalk.  A truck blared its horn as Bastard stepped onto the edge of the road.



Biter glared over his shoulder.  ``Cocky motherfuckers.  You'd think they would have \emph{more} appreciation for just how scary the wrong asshole with powers could be.''



``They feel safe,'' Rachel said.  She looked up and around, searching buildings for telltale signs.  ``Superheroes set up near here, probably.''



``You worried?''



``No.  Not worried.''



``Because you're confident you can deal, or because-''  He threw up his hands as Rachel leveled a stare at him.  ``Right.  Too many questions.''



``Doon, Colbie,'' Rachel addressed the dogs that accompanied Biter.  ``Nose.''



The Foxhound continued sniffing with his nose to the ground, but the bloodhound raised his head and barked.  It was a good bark, the sort that could carry over acres.



``Good dogs,'' she said.  ``Go.''



Biter held the leashes, and followed as the dogs moved down the side of the road.



Rachel kept Bastard moving at a slower pace as they followed, letting the gap grow.



``I feel underdressed.''



Rachel glanced down.  It was Cassie who had spoken.  She was warily looking at the people they were passing, drawing closer to Rachel and Bastard.  Her dog was a golden retriever, a little out of place alongside Bastard and the more imposing scent dogs they'd brought.  Well groomed to the point of \emph{shining}, though its hair was long.



Rachel looked down at the girl.  Dressed in a dark brown to Rachel's gray-white, Cassie had grown her hair long, tying it back into a ponytail, fuzzy earmuffs in place with the half-circle of metal beneath her hair.  The elbows and sleeves of her jacket and pants had been patched with a heavier material.  Her only nod to fashion was a spiked collar she wore, and a badge on her arm, which had a series of letters.



She'd asked once, and she'd gotten an answer.  \emph{Wag the dog}.  It was supposed to be a joke, but Rachel didn't get it, and the explanations had only confused her more.



Rachel took her eyes off the girl, spotting Biter in the crowd.  He, too, wore more spikes, but it was somewhat more blatant.  With the weather getting colder, he'd donned a hood, held in place by spikes that ran along the top and back of his head, puncturing the material.  The bear-trap jaw plate had been replaced with a more stylized version.  He was tall and imposing, but she tracked him more by the way the crowd seemed to move and shift to avoid him and the two dogs that zig-zagged in front of him, searching for the scent.



``I'm not the person to talk to if you're worried about that,'' Rachel finally said.



``I know.  I'm only saying it.  I can say, right?''



``Yeah.  You can say,'' Rachel answered.



But when she looked down at Cassie, the girl had her hands jammed in her pockets, her shoulders drawn in, half of her attention on Sunny.



``The clothes\ldots they're warm enough?''



``Yeah.  I'm snug.''



``Tough enough?''



``Yeah.  I'm seeing where you're going with this.''



``Comfortable?''



``Yeah,'' Cassie said.  She glanced up at Rachel.  ``I hear what you're saying.  But there's more to it than that.  The clothes can be all of those things, but I can still feel dumb because I put one of the dog's old collars on for a joke and now I've got people looking at me funny.''



``I like the collar.''



Cassie smiled as she lowered her eyes to the ground.  One of her gloved hands went up to the collar, tugging a bit.



Rachel wasn't sure what the smile or touching the collar were supposed to mean.  ``I said it before.  I'm not the kind of person who give you any good answers.''



``It's not a big deal,'' Cassie said.  ``Really.''



\emph{You were talking about it, so it's some kind of deal}, Rachel thought, but she couldn't think of a good way to say it.



And, apparently, Cassie wasn't willing to let the subject drop, now that they were talking about it.  ``Going from our neighborhood to \emph{here}, the people, the buildings\ldots''



``They'd look out of place if they came to our neighborhood, just like we look out of place in theirs.''



``That's not what I mean.  You don't feel like they'd be looking funny at you, even if Bastard wasn't here?''



Rachel shrugged.  ``I never feel like I belong anywhere.  This isn't any different.''



``Except when you're with us, right?  When you're home?''



Rachel shrugged.  ``I don't feel as out of place when I'm with you guys.''



Cassie smiled.  ``Good.''



They stopped at a corner.  People backed away to give them a wider berth as Bastard stopped walking, as if they were anticipating trouble at any moment.



Biter was on the other side of the street, trying to keep up as the dogs started walking in one direction, then stopped, reversing to move the opposite way.



``We're close,'' Rachel said.



``Yeah?''



Rachel leaned over in her seat, kicking Cassie lightly in the shoulder.



``Sorry,'' Cassie said.  The little smile didn't leave her face.



``Don't make me repeat myself,'' Rachel said.  She looked around, her eyes searching building faces for icons she could recognize, looking for people standing in strange places.  Nothing stood out.



She could feel the vibration as her power reached Cassie's dog, giving it strength, size, making it \emph{change}.  While the dog changed, she put four fingers in her mouth and whistled.



Heads on the other side of the street turned.



She only cared about one head.  Biter had looked, and she gestured for him to come back.



He made his way across the street.  He held Doon and Colby's chains with one hand, his other hand growing until it was almost as large as he was, fending off one car that was late in braking.



It was easier to use her power on the dogs when they were close.  The \emph{shudders }as her power reached and enhanced them got more pronounced as Biter approached.  As the size of the dogs increased, the people around them became more hesitant.  Four mutant dogs and two obvious capes were a threat.  It was easier to stand strong against a \emph{single} threat, to believe they could work together and overcome it.



Stupid, when that single threat was Bastard and they were just \emph{people}, but people were dumb.



They'd picked up the \emph{basics} of what had happened and how Scion had been stopped.  There was a message there, an unspoken understanding.  Maybe it was a part of the reason their body language had been so strange as she entered the city.  There was something happening, related to that, something complicated.  Not the kind of thing she was good at wrapping her head around.  She'd have to ask Tattletale.



She waited as the animals grew.  Again, she looked, searching for anyone that might be objecting to her presence here.  Heroes, villains, whatever-elses.



Cassie climbed onto Sunny's back.  Biter mounted Doon.



Rachel gestured, then whistled.



The animals leaped onto the side of a building.  Claws bit into the outside of the building face, into window ledges and windows, scraping stone.  One limb at a time, muscles shifting and rippling as they adjusted their weight, set each in place before moving with the next.



They reached the rooftop, and Cassie rolled off Sunny's back, landing on her back.



``I'm \emph{never} getting used to that,'' she said.  Sunny nudged Cassie with a gnarled snout, and Cassie laughed, rolling over onto her front and then hurrying to get to her feet.  ``Don't step on me, Sun.  Good girl.''



Rachel searched their surroundings again.



``You're looking for someone?''



``Trying to figure out how to do this,'' Rachel answered.



``We find him, we find her, we drag 'em back,'' Biter said.  ``Maybe we fish in their wallets, grab some cash, and we have Cass run in some place and grab some french fries.''



Rachel sighed.



``I could \emph{make} french fries.''



``It's not the same if it isn't distilled in the ambient misery of pimply faced teenagers in ugly uniforms.  Gotta have them limp with oil, loaded with preservatives, and coated in salt.''



``I refuse to believe those're better fries than I could make.''



Rachel shifted impatiently.  ``Are you two done?''



``No,'' Biter said.  ``I can't let this go, because bad fast food is \emph{important}.  It's a staple of society, and having ridiculous coffee shops and mass-produced food is a \emph{badge}, a way of showing that we've gone past the industrial age and into \emph{modern} society.  Seeing those glowing signs down there, it's a sign that humanity is actually recovering.  It'd be an \emph{insult }if we didn't partake.''



``I don't get it,'' Rachel said.



``You're not the only one,'' Cassie added.



``Let me put it simply,'' Biter said.  ``You two, you're happy where you're at?  You'd be content if you never had to set foot in a city like this?''



``Yeah,'' Cassie said.



Rachel shrugged.



``Yeah.  Me?  I'm okay where we're at.  \emph{For now}.  But I'm still sort of keeping an eye on the calendar.  No disrespect intended, boss, but I'm thinking I leave one day.  Maybe in a year, maybe in five.  I figure I've got to get back to the trappings of tried-and-true civilization at some point, or I'll go-''



A rumble shook the area.  A plume of mist rose into the sky a few blocks away.



``-Batshit fucking nuts,'' he finished.



``Cape fight,'' Rachel observed.



``Are you going to help?'' Cassie asked.



Rachel frowned.  They had the scent dogs.  They had the trail.  It would be easy enough to find their quarry and get out of here.



``The heroes are going to be on it,'' Biter said.  ``Whatever's going on, we get in the thick of it, things get more complicated.''



``I \emph{know},'' Rachel responded.  ``I'm not dumb.''



``But we're still standing here, which means-''



``We're standing here because I'm trying to \emph{think},'' Rachel retorted.  ``That looks \emph{big}.''



``And?  You don't care about people.  You hate people.  I quote, `people are stupid'.''



``They \emph{are} stupid,'' she answered.  ``And I\ldots don't like \emph{most} people.  Not the issue.''



``What \emph{is} the issue, then?''



She stared.  It had been a while since she'd stretched her legs, getting into the thick of things.  That wasn't it, though.  She'd spent her entire life being \emph{restless}, and now the restlessness was largely gone.



Taylor, then?  She thought of Taylor, and she couldn't help but think of the way people had stood together, as if bracing to fight back if she caused trouble.  Uniting against the bigger threat.



She wasn't dumb.  These days, she felt better about herself and who she was than she ever had.  But she admitted her failings.



I'm not \emph{articulate}d.



She couldn't put that idea into words like the others could.  \emph{Tattletale} could, obviously.  Taylor\ldots well, Taylor would have been able to.  Imp could put her thoughts into words, but she'd probably be more confusing than helpful.



It was frustrating, but it was a frustration she had come to peace with.



``That many people in trouble, bound to be some dogs and dog owners in there,'' Rachel lied.



``\emph{That's }your reason?  If you're going to talk like that, you might as well be a fucking \emph{superhero},'' Biter said.



She ignored him.  ``You don't have to come.  Bastard, \emph{go}!''



She could feel the shifting of Bastard's muscles, the little spot where one plate of calcified flesh dug into her knee riding up to mid-thigh.  He jumped with an explosive kind of strength, crossing the street and landing on another rooftop.



Even with Bastard absorbing the impact, it was a hard one.  She grunted.  The bruises and aches would be felt the next morning.



It was easier to maneuver here.  Probably had to do with the way the buildings were going up, everything following some plan or another.  There was \emph{order, }in this Boston.  It made the city feel less like a city, on some levels, with too much uniformity in areas, but she could appreciate how it made it easier to move around.



Another series of leaps.  Shorter distances, with no big drops.  Any pain she felt was from the first big jump.



She could see the capes fighting, down below.  A man was at the center of it.  He'd swelled in size until he was twice the height he should be, almost breaking apart, like a statue that had been dropped, only the biggest chunks preserved, hanging in mid-air in a vague human shape, high above the street.  Black ooze gushed from foot-wide cracks and divides in his body.  His flesh was dark brown, the edges of the cracks raw and bloody.



Even from her vantage point on the rooftop, she could hear his screams.  It was muffled, despite the volume, as though he were screaming while underwater, the effect amplified.



The capes were occupied – a very small few seemed to be trying to attack him.  The rest were working to keep the black ooze from spreading.



Rachel paused, watching.



Miss Militia was down there.  She had a containment foam gun, and was forming a short wall.



The screaming got \emph{worse}, and the man in the center broke in half, a crack widening in his torso until it separated completely.  More ooze, faster.  His lower body was almost impossible to see.



His hands went to his head-



\emph{Faces.  Mockeries.  Variations on a theme.  Reaching hands, supplicating.}



-The image was brief, but acutely familiar.  Rachel felt mentally disoriented in the same way she might be physically disoriented if she stepped forward and found the ground wasn't there.  Others in the area had staggered.  Miss Militia had dropped the hose for the foam gun.



Rachel gripped the chain that looped Bastard's neck.  When he was small, the same chain doubled as a leash.



Familiar, comfortable.  Reassuring, in the midst of this situation.



She'd had visions before, she'd even remembered one, after the fight on the beach.  They hadn't been like that.  It had been brief, and somehow broken up.



Something was \emph{wrong}.



Someone shot the black ooze man, and his collarbone splintered, cracks spiderwebbing up to an oozing fissure in his neck and the stump of one shoulder.  Rachel could see how more ooze was starting to bleed out from the site of the injury.



He reacted, looking down at the injury, then looking up.



He reached out, and the ooze below him shifted, moving in a singular direction as if it were flowing downhill.



The cape who'd shot him hurried to run-



\emph{A moment of uncertainty.  The population of this world wasn't reacting any further.  He attacked, they moved.  Again and again, they created the images.  They weren't afraid, and he was.}



-but stumbled as the mental image shook him.  He managed to get his footing, but the ooze moved faster with each passing second, and the delay had cost him.  It slopped around his ankles on its way past him.



The black ooze man moved his hand, and the ooze that was pouring from him became black \emph{fire}, spreading to alter all of the ooze it touched with a sound like the gas lanterns made, but a thousand times louder.  Things touching the fire burned, and the dark sea was briefly highlighted in oranges, yellows and reds.



The gunman who had attacked the ooze man dropped before he could react, his feet and lower legs burned away.  When he touched the black fire, there was a brief flare of orange flame before he was obliterated.



She had a sense of what she was up against, now.  She surveyed the battlefield.  The ground was rising into a crude bowl, containing the ooze, but a veritable waterfall flowed from the man's ruined midsection, and the rate at which the bowl filled was outpacing the rate at which the bowl grew.



There was a crash.  Sunny and Cassie had arrived.



``Biter?''



``Not coming.''



Rachel scowled, but left it at that.



``What's going on?''



``Trigger.  Something's wrong.''



``Trigger events can be plenty bad on their own.''



``Mm,'' Rachel grunted.



``Oh.  Yeah.  You know.''



``Mm.  You stay out of the way.  Black stuff is bad.''



She didn't wait for a response, ordering Bastard to head down towards the ground.  Why?  Hard to say, just like it was hard to explain the solidarity, or why she'd come in the first place.  There were people out there who functioned best with their brains.  Putting ideas together, analyzing the situation, rationalizing.  She wasn't one of them.  She functioned best on instinct.



Gut feeling?  If this fight continued like this, it would turn out ugly.



Miss Militia had shucked off the foam dispenser, and was backing up, shouting orders.  She pulled the trigger on a small gun, sending a flare skyward.



Rallying the troops.  Made sense.



The ooze man rose higher into the air, as she made her way down.  There were people on the fringes, cornered or caught where they couldn't freely maneuver.



Bastard's claws scraped against the side of the building on the way down, his front claws getting more traction than the rear ones.  He wound up swinging, his hind end descending while his front end maintained a grip.  Rachel was nearly flung off, but her hold on the chain kept her in place.  Bastard elected to drop the remainder of the way to the ground.



Another heavy impact.  The imminent bruising went from `I'll feel it in the morning' to `I'll be feeling this all next week'.



He was out of practice.  Chasing buffalo and bringing them down was different from leaping around a city.



But she was on the ground, free to run.



``Kip up!'' she called.



Bastard leaped, touching the side of the building, tensing and leaping from that point before landing on solid ground.  In the process, they'd circumvented a large pool of the black stuff.



They landed near one of the capes on the fringes, a man standing in a construction site, with enough stuff around him that he couldn't maneuver freely.   He was using his power to push at the ooze, a kind of telekinetic wind.  Her arrival had distracted him, and the wind had faltered.  The ooze encroached.



She extended a hand.



He glanced at the ooze, then at Bastard, and sided with her.  He took her hand, and used his power to help himself up, landing behind her.



She could see movement out of the corner of her eye.  Tentacles, pitch black, reaching out of the ooze that poured from the man's body.  Like the fire, it spread, altering all of the ooze it touched to make it the same.



``Up!  Rooftop!'' she called out.



Bastard leaped, ascending by leaping from one wall to the next.  By the time they were halfway up, the tendrils were almost touching them.



They reached the last jump, leaping to the lower of the two rooftops, and stopped.  They'd been snared, suspended over the street, the rooftop ten feet in front of Bastard's front claws.



Cassie was approaching, moving along rooftops to try and get to them.  Below the rooftops, the entire neighborhood was a shifting morass of black fronds,grasping, seizing what they could, crushing.  Fire and the lights of other powers were visible on the opposite side of the battlefield.  Miss Militia's group.  A flamethrower-



\emph{He tried to push the feelings away, but they were seductive.  A spiral, where the feelings were both the torment and the balm that soothed the torment.  Stopping was daunting}.  \emph{He had been wrapped up in them, and now it was something else.  He'd never dealt with something like this.  For hours, days, he'd been reveling in emotion, and now he couldn't stow it away, even as he experienced trauma for the first time}.



-torched the worst of the tendrils, keeping them at bay.  The fire stopped as other capes stepped in.



Rachel felt a frond seize her wrist.  She pulled, and it didn't give.  Cassie wouldn't make it in time.



The telekinetic wind shifted from focusing on the fronds to focusing on Bastard.  Pushing him in one direction, getting his claws closer to the rooftop.  One and a half feet closer, two feet\ldots



At the same time, the rooftop changed.  It twisted, inching closer to them.



Rachel gave her companion a bit more power.  Size at the expense of flexibility.



Bastard extended his front claws and found a grip.  He pulled himself and his riders closer, and the tendrils that encircled him went taut.  All of his strength, and he couldn't manage another inch of progress.  Claws left gouges in the rooftop.



Other tendrils encroached.  There was no ooze on the ground, now.  All of it was alive, a singular writhing mass that extended from the man above them.



Distant gunshots sounded.  They jerked forward, and Bastard got one claw on the edge of the roof.  More traction.



Two more gunshots.  They were free.  Bastard made it three steps before the black tentacle around Rachel's wrist pulled tight.  He took her sudden movement as a command and stopped, turning, his head moving so he could see any gestures or instructions.



A red dot appeared on the tendril that gripped her.  Another distant gunshot, and it was severed.  Ooze splashed onto the rooftop.



``Go!''



Bastard moved.



Tendrils became fire in that same flowing transition, and the flaming liquid descended, covering the streets and buildings below them.  There were flammable materials on some of the rooftops, where tall buildings were being extended to be higher, and black flames rose.



High above them, the man continued to fall apart.  Barely any fragments were larger than a fist, now.  There was only the upper half of his head, a chunk in his chest.  His legs were a pillar, framing the flow of the ooze that continued to spread beneath him.



Capes had retreated to higher ground, but it wasn't a refuge.  The ooze would change again.



Common sense told her she shouldn't get any closer.  Instinct told her otherwise.



She directed Bastard to a lower rooftop, then one that was lower still.  A pair of kid capes, fending off the spreading black flames with a combination of powers.



There wasn't time to be \emph{nice} about it.  She grabbed one, had Bastard grab the other.  They ran for higher ground as the liquid fire became \emph{mist}.



It reminded her of Grue's smoke.  It spread to fill the air, and it moved too fast to avoid.  Consuming everything, \emph{covering} everything.  The fires seemed to have gone out, or the black fire had overtaken any normal fire, but the damage was there.  There were places where Bastard would fall through if he landed, balconies and rooftops.  hazards.  They were harder to see now, too, behind the mist.



If he turned it into fire or tendrils \emph{now}\ldots



``Up!''



The heroes were hesitating to attack any more.  Easy to see why.  Every bit of damage seemed to increase the amount of ooze by a hell of a \emph{lot}.



He wasn't dying, he wasn't \emph{stopping}.



She ordered Bastard to higher ground, and the telekinetic wind helped them rise, where the added weight of the two kids slowed them down.  The tallest building was near Miss Militia, so she circled around the area where the fight was taking place, constantly moving higher.  A balcony nearly collapsed beneath Bastard's weight.  She misjudged a jump, urging Bastard on, while forgetting that she'd made him stronger and less agile.



Down there, somewhere on the ground, Miss Militia was in the midst of the smoke, her team holding it at bay.  She seemed to come to a decision.  Her rifle became something else.  A cannon, fixed to the ground.



She shot into the black mist with a rocket.  The rocket seemed to grow to twice the size as it flew.  The explosion was dramatic, noisy, and distracted Bastard mid-landing, making him stumble.  The explosion consumed the ooze man entirely.



The amount of smoke flowing out around the man\emph{ doubled}.



Two more rockets hit the same point, each one growing as it moved.



The smoke cleared.  The dust and smoke from the explosions slowly cleared.  By the time the area was visible enough to check on their enemy, the black mist was starting to clear as well.



He'd been stopped.



The visions, they'd been broken up, too recent.  She wasn't forgetting them.  The power, too\ldots he'd been strong.



He'd been-



\emph{A man in a white hood and cape stood there, the tension in his body swiftly stopping.  He had no expression, only a green and blue glow beneath his hood, but his body language was clear.  Shock, defeat.}



\emph{A flash of golden light wiped him out of existence.}



-too strong.



She started to turn her head, looking for the source of the voice, and felt the disorientation that had accompanied the visions.  Her ride-alongs weren't in better shape.



It wasn't over?



Bastard's head turned.  His ears perked up.



Instinct.  She urged him towards whatever had gotten his attention.



She could hear it, now.



``Hey,'' the wind-maker said.  ``What-''



He stopped when he heard the same sound.



Screaming.  As if from underwater, getting louder with each moment.



There was somebody on a rooftop, in the midst of a garden, screaming.



Her arm broke in half, and ooze began dripping from the injury.



Bastard collided with her, and she broke apart, ooze flowing like a wave, tossing them aside.  It was defensive as much as offensive.



Except it seemed to be hurting its host more than anything.  The force of the flowing ooze was damaging her body, tearing her apart.  Her eyes were gone, with only dark sockets streaming more fluid.  When she opened her mouth, more erupted forth, flowing.



``\emph{Again,}'' Rachel whispered.



Bastard found his feet, readying for another attack.  She could feel the tension as he prepared to leap.



\emph{Just have to break her enough.}



The ooze froze into jagged crystal.  Bastard's leap failed, and he nearly bucked his riders free.



The freezing had spread through the ooze that covered the woman, and the jagged spikes of black ice tore through her upper body and head.



For long seconds, things were still.



And then the woman came to pieces.  The ice broke, and Bastard pulled himself free.



``Jesus,'' the wind-man said.



Rachel was silent, watching the back of Bastard's head.  He hadn't reacted like he'd heard more screaming.  Was it over?



``Hey kids, are you-'' the man started.  He was silenced as Bastard leaped, retracing his route to the ground.



More hard landings, but she was already resigned to the aches and pains that would follow a fight.



When they touched solid ground, Miss Militia's entire group was waiting.  Vista was there, along with one of Taylor's teammates from Chicago.



Bastard landed, and Rachel was careful to keep a distance.  Miss Militia stepped forward, and Rachel directed Bastard to back up a little.



``We going to have a problem?'' Rachel called out.



``No.  No problem,'' Miss Militia said.  ``I'm coming closer, okay?  We're good.  There's an amnesty.''



``Don't know what that means.''



``There's a deal.  Everyone gets a second chance.  We don't have a problem with \emph{anyone}, until they do something wrong.''



``I'm not a villain anymore?''



``Not unless you want to do something villainous.''



Rachel nodded.



Miss Militia approached.



``It shifted to a new host,'' the wind-man said.  ``That was definitely another one.''



Rachel gave a push to the kid she'd slung over Bastard's shoulders.



``Get down,'' Rachel said.  ``Bastard, drop it.''



Bastard let the boy he was holding drop, along with a fair amount of slobber.  The boy hurried back.  The girl was taking more time to find her way to the ground.  Rachel grabbed at her arm, and the girl flinched.



``You dealt with it?''  Miss Militia asked, stepping closer to give the girl a hand.



The wind-man wasn't moving.  ``It dealt with itself.  The power destroyed the host.  That's number two on the list of things that aren't supposed to happen.''



``Shit happens,'' Rachel said.  ``World makes a lot more sense when you accept that.''



``This is a little different from the everyday sh-tuff,'' the man said.



Miss Militia nodded, her eyebrows knit together in concern.  ``This makes four.  Almost a fifth of the regular triggers we've heard of.  Two in three days.  One's still loose, the others died or destroyed themselves.''



``Hey, wind-man,'' Rachel said.  ``Off.''



``I'm just waiting for Gloss to get down.''



``\emph{Off.}''



He heard something in her tone and moved, using his power to hop down.



``Hellhound-'' Miss Militia said.  Rachel gave her a hard look.   ``Um.  \emph{Bitch}.''



``If you're going to fucking give me trouble after what you said before, then-''



``\emph{No.}''  Miss Militia said.  She raised her hands, showing she was unarmed.  The mortar was a distance away.  ``Thank you.  \emph{That's} what I wanted to say.''



Rachel shrugged, averting her eyes.  She couldn't help but feel surrounded, here.  ``I was looking for you anyways.  This is your territory?''



``That's a little complicated.  The-''



``You work here?  Do the superhero thing?''



``Yes, but-''



``Then it's yours,'' Rachel said.  Others had told her she could sound hostile in situations like this, so she tried to speak like she would to a dog that hadn't been exposed to humans.  Gentle, acknowledging the fact that it couldn't understand.  The sound was more important than anything.



``Um, I suppose,'' Miss Militia said.



``It is,'' Rachel said, trying to measure her tone, suppressing her irritation.  ``If someone else is in charge, you tell them this instead.  Some fuckstick came into \emph{my} fucking neighborhood, cozied up to his old girlfriend, then waltzed with their kid.  Came here.  I was looking for the asshole, and I wanted to let you know before I went to collect them.''



``Okay,'' Miss Militia said, sounding a little more authoritarian.  She glanced at the wind-man, who had his hands clamped to the boy's ears.  ``That's-''



``Okay?''  Rachel gave Bastard a light kick, indicating he should go.



``-Problematic!''  Miss Militia raised her voice.



But Rachel was already leaving.  She heard Miss Militia's voice, swearing, running footsteps.



Didn't matter.  A glance to the rooftops indicated that Biter had arrived.  He had a man and a little boy with him.



She pointed, and she could see a nod on Biter's part.



\sectionbreak



From civilization to nature.  She could relax.



``Didn't realize it would be that serious,'' Biter said, when they'd slowed.



Seeing Bastard panting, Rachel led him to the water.  The other dogs followed, eager for the chance to drink.



``Not an issue.''



``See, this \emph{is} an area where you should get on my case, get mad that I didn't help.''



``I told you it was fine,'' she said.  ``So it's fine.  Who the fuck doesn't say what they mean?''



``Most people?'' he asked.



``Most people are morons,'' she said.  ``Bitching about wanting french fries or whatever.''



``A strong \emph{recommendation}, not a\ldots bitch,'' he said, stumbling over the last word.  ``Thank you, by the way.  I appreciate your willingness to stop.''



``Kid needed food anyways,'' Rachel said.  She looked at the boy who was riding with Cassie.  The girl had opened her jacket and zipped it up so it held him to her.  ``He good?''



``A little spooked, tired.  It's a long way to travel, even with breaks,'' Cassie said, ``But I think he's mostly good?''



She'd made it a question, looking down, and the boy nodded.



``Issue's handled.  Take the kid to his mom, take the dad to a cell.  We figure out what we do with him tomorrow.''



``Right,'' Biter said.  ``And you?''



``Going for a ride,'' Rachel said.  She jerked her thumb over her shoulder.



``Oh,'' Biter said.



``Say hi to her for me?'' Cassie asked.



Rachel nodded.  ``Anything else?  Stuff?  Problems?''



``No,'' Biter said.  ``Thanks for the burger-stop.''



Rachel shrugged.  She gave Doon a bit more power, to ensure he got the rest of the way home, then hopped off Bastard's back.  She led him by the chain as she walked down the path.



The fields had tall grass, and the light frost hadn't done much to dampen the effect.  In the afternoon light, it glittered and sparkled.



There'd been a problem.  She hadn't missed that.  Some new powers weren't working the way they should.



She'd have to talk to Tattletale about it.  Figure out what it meant, and whether she needed to do something in case one of her people went down that road.



She was losing Biter.  This wasn't the life for him.  He was loyal, he wasn't dumb, and he wasn't a bad lay, if she was in the mood for that.  Didn't, unlike some, make it more than it should be.  He took it in stride.



She'd barely had time to register that he was going, before the trouble started.  It bothered her more than it should.



People came, people went.  There were so many reasons for it all.  It was exhausting to keep track of.  Sometimes impossible.



She led Bastard down a path towards the mountains.



She stopped at a spot where the path crested a hill, between two peaks.  Not all the way through the mountains, but far enough that she could see the ocean.  The Bay.



Bastard knew the way.  His flesh was sloughing off, and he was slower, but he was adroit enough to navigate the rocks.



At the side of one mountain, here, a tree had fallen into a `v' where another tree stood.  with a glimpse of the spot where the city should be.  Water had filled the cracks where the landscape had been ruined.  When the trees had had leaves, they had framed the view.



At the top of this hill, rocks had been rolled into place, some with the help of her dogs.



She sat down with her back to the biggest.



Her hand settled on one rock, and she gave it a rub, like it was a dog's head.  Some left like Biter was leaving, while others were gone forever.



Bastard growled, then barked.



``Who's there?'' Rachel called out.  She sat forward, looking towards the path.



``Am I intruding?''



Rachel tensed.



``If you'd like,'' Miss Militia said, stepping into view.  Her eyes surveyed the scene.  ``We could talk somewhere else.  If you want to respect the sanctity of this place.''



``It's a good sitting place.  If we have to talk, we can talk here.''



``Sounds good.''



Bastard growled.  Rachel gestured, giving the order, ``Stand down, Bastard.''



Bastard sat, visibly relaxing.



Miss Militia nodded.  ``Just so you aren't surprised, you should know I brought Vista.  Wanted to cover more ground, catch up to you sooner.  Didn't work out, with us having to stop to double check for your tracks.''



Rachel shrugged.



``Hi,'' the blonde girl said.  ``I'm kind of glad I was brought along.  Seeing home again, kind of.''



``Sure,'' Rachel said.



``A memorial?'' Vista asked, laying a hand against the largest stone.



``Yeah.''



``Can I ask who for?  Or is that a dumb question?''



``Dumb question,'' Rachel said.  She leaned back, resting her head against the stone behind her.  When Vista didn't respond, Rachel relented.  She pointed at where the two trees rested against one another by the cliff face.  ``When the weather was warm, there was a bee's nest there.  The buzzing doesn't bother me as much as you'd think.''



``Oh.  Well, listen, last thing I want to do is disrespect that.  I've said goodbye to too many people, myself.''



Rachel nodded.  ``Sure.''



``If you wanted, I could shape them.  Been working on the little details.  Could do a statue, or letters.''



``No point,'' Rachel said.  ``Anyone who's been here and seen them knows who they're for.  I don't care about the others.''



``Gotcha,'' Vista said.



Vista found a seat with her back to the rock.



``We need to talk,'' Miss Militia said, leaning against the cliff wall, arms folded.



Rachel nodded.  ``Okay.  Talk.''



``I can't let you handle a custody dispute like you handled\ldots that.  Attacking someone, beating him up, hauling him a hundred miles away to another city.''



``Kid was mine to look after.  The mom was mine to look after.  I'm supposed to just let it happen?''



``There are options.  You could talk to us, ask.  We'd find a middle ground.''



``Talking is a pain in the ass.''



``It is.  I've been a team leader for a bit, now, and I agree one hundred percent.  Worst part of the job.  But it's better to talk than to make enemies, isn't it?''



Rachel sighed.  ``Sometimes I'm not sure.''



``The amnesty is your best friend right now.  If you don't want to do the talking, maybe you can ask Tattletale, and \emph{she} can?''



``We don't talk as much.  Different places, doing different things.''



\emph{People leave.}



``It would be an excuse to keep in touch.''



Rachel shrugged.  ``If I don't deal with my own stuff, what's the point?  I'd rather be in control.''



``What do you mean?''



``It's all about the rules.  Rules you understand, rules you don't.  Being in the city, I was sort of realizing just how many there are.  Codes, deals, even the way we dress, apparently.  Hard to keep track of.''



``I understand that.''



``You want me to ask Tattletale to handle shit.  But I'd prefer to handle my own shit.  That way, I know what's what.  There's no ugly surprises.''



She stopped, rephrased, ``There's \emph{less} ugly surprises.  This asshole that's working for me?  All of a sudden, he tells me he's not happy.  \emph{French fries} are more important, or something stupid like that.  I dunno how to argue with him, because I don't \emph{understand} it.  They're supposed to be some symbol or shit like that and I don't get it.''



``Been there,'' Vista said.  She looked cold, even with the tights she wore with her costume.  She rubbed her legs, then hugged them.  ``Losing people, not being able to understand \emph{why}.''



``If you wanted, we could connect you to someone you could talk to,'' Miss Militia said.



Rachel shrugged.  ``Talking bugs me.''



``Okay.''



But as much as it bugged her, she found the words spilling out.  ``I can get him wanting to go.  I don't understand it, but he says he needs that shit, so long as I'm handling stuff on my own, I can maybe grab him some damn french fries, keep him from leaving for a little while.  Maybe give him some more time here and there so he could go buy more.  Or whatever.''



``I see what you're getting at.''



``And \emph{some}\emph{idiots},'' Rachel said, banging her head against the rock behind her, a little harder than she'd intended, in a spot where the rock jutted out.   The sharp pain brought tears to her eyes.  ``Are even harder to understand than the motherfucking french fry thing.''



``Yeah,'' Miss Militia said.



Rachel rubbed the stone to her right.  \emph{Brutus}.  Bastard approached and laid his head down on the rock, and she gave him a good scratch.



``The rules are changing, breaking down,'' Miss Militia said.  ``Powers, groups, between capes.''



``Shit happens,'' Rachel said.  ``I said something like that earlier, didn't I?''



``You did.  But I don't agree.  I don't want things to break down.  I don't want conflict.  We were on opposite sides, but we were \emph{there.  }We went through a lot of the same stuff.  Can we not end this as enemies, fighting because of some misunderstanding?''



Vista spoke, looking out at the bay.  ``Make it a Brockton Bay thing.  We're motherfuckers, we're survivors.''



``Not sure I get it.  But I don't fucking trust people.''



``\emph{She} wanted us to work together,'' Miss Militia said, emphasizing the `she'.



Rachel looked up, but Miss Militia was staring out at the water.



Her voice was a growl.  ``If you're fucking manipulating me, I'm going to have Bastard chew you up and spit you out.''



``No manipulation.  Look, let's get down to brass tacks.  The basics.  What do you \emph{want}, Rachel?''



``Me and mine get left alone.''



``I can agree to that.  We'll leave you alone, we'll help make sure others leave you alone.  But, if we're making our own rules, between us, \emph{my} rule is I want to know before you do anything outside your territory.  Let me know, and you can ride along, so you're clued in and not missing anything.''



Rachel nodded, giving Bastard another scratch.  ``Sure.''



``A starting point?''



``A starting point,'' Rachel agreed.



``I talked to Tattletale before I came.  You should get in touch.  She had some stuff she wanted to discuss.''



Rachel nodded.



``Can we trust each other?''



Rachel frowned.



Trust.



She'd lost hers right in the beginning.  Left alone in an apartment, to starve and scald herself.



Here?  Now?  Seventeen years later?  After any number of betrayals, great and small?



She was aware of the tall stone behind her.



``Sure.''





