





\emph{Head high.  Shoulders square.  Walk like you know where you're going, like you belong.}



He'd had the best teachers around.  Public speakers, flirts, con artists, actors, thieves, magicians, and cutthroats.  He'd been educated in history, foreign affairs, management and internal affairs, intelligence, and codebreaking.  He'd learned from the best in medicine and poisons, in parahuman studies, in accounting and trade, the sciences, strategy and tactics in military, government and business roles.  He knew how to make things, and how to fake them.



Even in the little things, hobbies to some and unlikely careers to the foolhardy, he'd achieved some degree of competence.  Music, singing, art, prose and dance.  All it took was the right teacher, a \emph{hungry} eagerness to learn, and time.



One could not lead, after all, with one eye closed.  Some could lead while admitting some ignorance in one department or another, but he wasn't \emph{some}.



He was a jack of all trades, master of quite a few.



Two of those `few' accompanied him.  A woman in a white bodysuit walked just to his left.  He'd picked her because she had a natural grace and self-assurance, but her name escaped him.  He could remember how he had found her.  She'd been a hero, and she'd watched her team die in the aftermath of the attack.  Lost, helpless, broken.  Now she stood tall, back straight, joking and laughing with her companion.



The \emph{real} her was numb, locked in a cage, but that was secondary to the point.



The other was numb too, but not in the same way.  He was very much \emph{himself}.  If he was disconnected, it was a natural sort of disconnection, the sort that had happened billions of times throughout human history.



But the man was talented.  He wasn't acting like he belonged, because he \emph{did} belong.  He was a free spirit, and the world was his oyster.  He could put on a different face, and it wouldn't be a mask, but a \emph{role}.



He was a warrior, wearing heavy armor.  Gruff, rugged, with a beard and the stylings of a viking, complete with fur as part of his costume.  When the woman in white found herself off balance, stumbling, he picked his words to counterbalance it, changing the thrust of their interaction.  He teased, leaving the road open for clear and unambiguous responses, making small jokes so she could laugh and find her mental footing.



In a very one sided way, he was sustaining and supporting what appeared to be a very natural dialogue between longtime friends.



A pair of heroes rounded the corner, glancing at them.  The `viking' was in the midst of making a joke.



``\ldotssix different flavors of sausage.''



The woman frowned.  ``That's a non sequi-  oh.  \emph{Oh.}''



Watching the woman turn red, seeing the viking laugh, he couldn't help but join in on the laughter, a chuckle.



The viking slung an armored arm around his shoulders, making him stumble.  ``You actually laughed!''



``It \emph{was} a little funny.''



``A \emph{little}?''  the viking asked.  He nodded at the pair of heroes as the two groups crossed paths.  He offered the words, ``Hey, Ironscale.  `Sup?''



``I know you?'' one of the pair asked, stopping in the middle of the hallway.



The viking was still walking, but turned around to walk backwards as he called out, ``Costume change to fit in with the new era, my friend!  You'll figure it out, and I'll be \emph{very} upset with you if you don't!''



They rounded the corner.



``Did you know him?  This Ironscale?''



The viking smiled.  ``Ironscale?  No.  A face in a file, at some point.  But I have a good memory.''



\emph{Liars have to.}  ``It was dangerous, baiting him.  Better if we don't draw attention.''



``Trying to \emph{avoid} attention is attention-getting enough.  You brought me on board for my skills, Teacher.  Trust me to use them.''



Teacher sighed.  ``Fair.''



The smile disappeared from the viking's face.  ``You're nervous.''



``I'm \emph{inclined} to think I'm paranoid,'' Teacher said.  ``I try to convince myself otherwise.''



``Why?''



``If I'm going to explain, I have to ask,'' Teacher said, ``what's the difference between paranoia and nervousness?''



``One is a state of mind, the other is a temporary state of emotion?''



``The former is a kind of madness,'' Teacher said.  ``Popular culture has twisted it, but popular culture has twisted \emph{madness} in general.  They make it funny, they romanticize it, or they make it exaggerated.  But true mental illness is nothing to laugh at.  I stayed in the Birdcage for some time, I've seen scary things, and I've become numb to a great deal, but going mad is perhaps the scariest.''



``Yet you corrected me when I said you were nervous,'' the viking said, strangely soft spoken given his frame and earlier demeanor.



``The alternative to being a madman might be worse,'' Teacher said.  He shook his head, as if stirring himself from a spell.  ``What were we talking about?''



``Is this your first time in the infiltration role?''



``In a meaningful capacity?  Yes,'' Teacher admitted.



``You could have stayed behind.''



``I'd like to handle this face to face, build a rapport.''



``You could have let me do that for you, build your rapport for you.''



``I think that's a dangerous road to travel.  Will we do that the next time?  And the time after that?''



``I don't see why not.''



``I could not be a leader if I didn't actually \emph{lead}.  Besides, I don't trust you.''



``You think I'll stab you in the back?'' the viking asked.



``I think \emph{everyone} will stab me in the back,'' Teacher said.  He sighed.  ``Paranoia, again.''



``If you keep walking down this road, then they probably \emph{will} stab you in the back.  That joke, `it's not paranoia if everyone really is out to get you' could be a self-fulfilling prophecy in your case.  Maybe you're even doing it on purpose.''



``You might be even smarter than you let on,'' Teacher said.  ``I'm glad I didn't brainwash you.''



The man chuckled.



Teacher shook his head.  ``I aim to change course.  If they plan to ambush me at some point down that road, they'll be waiting a long time.''



``That's simple enough, when you only have one enemy.  But when you have as many as you do\ldots''



``It requires a more blatant change of course to throw them off.''



``If you say so.  You seem to have things in hand right now, at least.  This way.  We'll be entering an area with higher security, so be on guard.''



Teacher glanced up at the camera.



``You don't trust your people to handle it?''  the viking asked.



Teacher shook his head.  ``I trust them.  Put enough on a job, and the only one who could work around them is Dragon, and Dragon isn't here, nor is she able to work against me.''



``You think.''



``I \emph{think}.  Let's not underestimate Big Sister.''



``In case you were wondering, I think that's intelligence, not paranoia,'' the viking said.



The viking tapped his phone against the panel by the door.  Teacher tensed.  Waiting.



The light went green, and there was a sound as bolts moved.  He let himself relax.



The viking spoke in a low voice as they entered.  ``Level one security.  Not cells, exactly, because the people here haven't technically done anything wrong, and the amnesty protects them, but they can't be allowed to freely wander the building, with sensitive materials and unmasked heroes around.''



``Yes, they can't have troublemakers walking about, can they?''  Teacher asked, with a note of irony.



``The people staying in the level one security area get chaperones when they want to go somewhere, and cameras keep an eye on them\ldots usually.''



Teacher glanced around.  Where there had been offices in the previous area of the complex, this area was residential.  Some of the doors here were open, showing clean apartments with everything neat and in order, waiting for an occupant.



Some, though, were inhabited.  Each resident had made the space their own.  One appeared to be layered in a crusting of junk – bottlecaps and glass shards arranged in kaleidoscopic patterns.  Another was all black leather and chrome, smelling faintly of an expensive aftershave.



They stopped at the doorway to another room.  There was little doubt in their minds after they saw the interior.  A folding screen with a dragon print and women in kimonos on it was below iconic pin up images, modern and dated.  50's pin up girls alongside recent celebrities. The way they were organized and clustered, it seemed somehow less like decoration and more like\ldots character studies?



From their vantage point, the corner of a four-poster bed was visible.



``Ingenue,'' Teacher called out.



Feet swung out over the side of the bed, and she was standing in a moment.  She stopped short when saw him, pouting, one fist against her hip.  Dramatized, artificial.  Even the way she dressed, it was the same, a silk bathrobe that was short enough to be borderline indecent.  Always putting on a show, and not in the sense of showing \emph{skin}, but acting, putting on a mask.



``You got my hopes up.  It's \emph{you},'' she said.  ``Dressed up like a wizard, maybe, but it's not \emph{that} good a disguise.''



``Doesn't have to be.''



``Shame on you, not even calling a girl before you show up unannounced\ldots but you were never very classy.''



``No, I'm afraid not.  If you'd like to talk to \emph{Marquis}, I'm sure he could oblige on that front.''



``He switches from the aristocrat to the low born commoner as it suits him.  Split personality.  Is that what this is all about?  Are you planning on gathering us all together again?  Clinging to the past, Teacher?''



``I was planning on visiting him, but not for the past, and not to gather anyone.  Not in that sense.  I'm touching base with certain people, nothing more.''



``Why?''



``Getting the lay of the land,'' he said.  He saw her put on a shocked expression, then cut her off before she could speak, ``\emph{Assessing the situation}, Ingenue.  There's a great deal going on, and I'd rather work with known quantities before I start interacting with foreign ones.''



``Should I ask \emph{why now}?''



``For someone who is feigning disinterest, you're asking an awful lot of questions.''



``I'm \emph{bored}, Teacher.  I'm even losing interest in Chevalier, and he doesn't find time for me, unless it's to make sure I'm being a good girl.''



``Do you fancy a trip, then?  A walk outside?''



``My jailors, who seem very invested in declaring they aren't actually jailors, might take umbrage.''



``I'll have you back by curfew, if you're still interested by then.''



``You're \emph{planning} something,'' she said.



``Of course.''



``Tell me,'' she said.  She put her hands into the pockets of her dressing gown, which were too small for her whole hands.  ``And maybe I'll go on this field trip of yours.''



The viking leaned in close to Teacher, ``Time.  If they did notice anything\ldots''



He trailed off.  There was no need to spell it out.



Teacher nodded a little, but he continued, unruffled.  ``I'm looking to put together something \emph{bigger}.''



``Bigger than?''



``Than any of the teams currently in operation.  Than any of the powers we've seen yet.  Call it megalomania, if you will.''



``Why?  Before you say anything, you should know that `because I can' isn't an answer.''



``It was never the answer.''



``You've done a lot of things, and everything indicates it was for that very reason.  Cas Raul?'' Ingenue asked.  She was relaxing now, the guise dropping.



``I've done a lot of things, agreed, but there were always other motivations.  I admit, I was younger then, the plans were cruder.  But the plans still worked and there \emph{was} a goal involved.  For some time, I'd been gathering information and putting pawns in place, starting to get a feel for how the dynamic was all put together.  The connections between people and groups, the powers at play, the choices being made and \emph{why} those choices were made.''



``And this leads to the murder of a vice president how?''



``Killing a man that prominent sets everything into motion.  That motion lets me see things from different angles, filling in the blanks.  I needed to do something big to disturb the dynamic enough that I could glimpse the \emph{real }big picture and fill in the blanks.''



``Big picture.  You're talking about significant things, again.  On par with killing a vice president and a prime minister.''



``This is a little more impressive.  In any event, I got the information I wanted with my play, first the national death, then the international one, to see the effects and plot things out on the global scale.  I was all set to act on it when I got arrested.  I was left with years to think, to study and improve myself.  I plotted our release to keep myself sane, and to keep things in motion.  You \emph{are} welcome for that, by the way.''



Ingenue shrugged.



``I got free, then I took action, equipped with my new knowledge.  It didn't take long for opportunity to present itself, and now I'm very well set up.  I found the missing puzzle piece and I made it my own, mystery and all.  Some of their assets are my assets now, and I have the footing to do something else entirely.''



``A subject you're dancing around.''



``Nothing particularly criminal, believe it or not.  But it would be silly of me to tell you everything if you were going to refuse my invitation and then tell your chosen boyfriend at the first opportunity.''



``We know each other, Teacher.  You don't \emph{really} think I'm that one-note.''



``No.  No, I don't.''



``Yet you won't tell me.  You're a \emph{tease}, Teacher.''



``I'm--''



His phone beeped.  Two high notes, in quick succession.



``An alert?'' the viking asked.



``I may have overestimated my collective's ability to keep us out of sight,'' Teacher said.  ``Miss?''



The woman in white raised an eyebrow.  ``No \emph{immediate} threats.  But it's hard to tell.''



He nodded, glancing at the door.  \emph{No police officers in power armor}, he mused.



``We'll go,'' he said.  ``Ingenue--''



He stopped.  He'd turned, and she wasn't there.  Invisibility wasn't one of her powers, but-



The dressing gown flew into the air, draping itself over the top of the dragon-print folding screen in the corner.  She was on the other side.



``I see you've decided that you're coming.''



``I'm bored,'' she said, from behind the screen.  ``They can give me my art, good food, entertainment, chaperones to plays, but I want \emph{one} thing, and they won't give him to me.''



``If you're leaving to kick up a fuss, so he has to come after you\ldots''



``I'm done with him,'' Ingenue declared.  She stepped out from behind the screen in a dress with a high lacy collar.  ``His loss.  You know, I'm aware my boyfriends have had a run of bad luck.  I'm not \emph{oblivious}.''



``You're cursed,'' the viking commented.



She smiled, leaning over her dresser to peer at herself in an oval-frame mirror, snatching up some lipstick to touch herself up.  ``I wouldn't say that.  A good love story ends in tragedy, doesn't it?  Outcome aside, isn't it glorious in its own way?  I've had more than a few of these stories.  I've suffered heartbreak, even, but I'm tougher than I look.''



``So Chevalier has slipped the noose?''  Teacher asked.



``More apt to say he's stepped out of the frying pan,'' Ingenue said, running a brush over her jaw-length hair, ``The only ones who end up worse than my boyfriends are my \emph{ex-}boyfriends.  It's so sad.''



She turned around, hair and makeup done, and there was no warmth in her eyes.



``His loss, as you said,'' Teacher commented.



She frowned a little, but her eyes didn't waver or change in how cold they seemed.



``They're coming,'' his student said.  ``Two.  Same way we came.''



``Shall we?''  He indicated the door.



They left.  The moment they were in the hallway, the doors at the end opened.



Dragon's Teeth.  Civilians with power armor and training.



His power was a problem, here.  He produced thinkers and tinkers, but they were low level, limited in scale.  A precog that warned of danger a few seconds before that danger arrived wasn't so useful.



Still, it meant the Dragon's Teeth were more surprised than they were.  A chance to bolt for it.



``I worked so hard to get down to security level one,'' Ingenue pouted.  ``Dashed in a moment.''



``I didn't think you were planning on coming back?'' Teacher made the statement a question, leading the way around a corner.  \emph{The stairwell will be locked down, but if we can find an apartment to duck into, we could slip out.}



``A girl likes to hold on to her reputation,'' Ingenue said.  ``Even if that reputation is merely `dangerous' and not `cataclysmic'.''



\emph{With those doors and the stairwell barred, we have nine escape routes.}



``While I was scouting the area,'' the viking said, ``I heard a few people making noise about you.  Word was out you'd scuffed the ground with your toe while batting your eyelashes at one of the jailors, and they wanted to raise you to back to `cataclysmic'.  Well, they said `level two security', so maybe something less severe.  What's between dangerous and cataclysmic?''



``I think it would be unwise to say, for fear of offending our colleague,'' Teacher said.



``I think so too,'' Ingenue agreed.



``If it makes you feel any better, I think they're badly underestimating you,'' Teacher said.



``Kind of you to say so, but I'm not dangerous.  Mere slander and lies.''



\emph{Obession and self-delusion.  Her particular madness?  Or is she better at acting than I suspected?  Is it merely that she's told herself these lies so often she believes them?}



They found an empty apartment and eased the door closed.



Teacher reached into the front of his robe and withdrew a disc of metal.  He tossed it to the ground.



The lights fritzed out.  It wasn't merely a blackout, but a momentary, violent crackle that traveled throughout the apartment and across the floor.



The teleportation device didn't activate.  The armor around the man in the viking outfit fizzled and disappeared, panel by panel, revealing itself as the hologram it was.  He wore only knee-length, skintight shorts.



``They're more on the ball than we anticipated,'' the near-naked viking said.



``Run interference?''



The man nodded, and His flesh began distorting.



Osmosis of a full human being.



``I hope that wasn't the full extent of your escape plan,'' Ingenue said.  ``I'll be peevish if I get moved up to another security quadrant because of this embarrassing little stunt of yours, an escape attempt lasting all of five minutes.  I \emph{hate} being peevish.''



``There are\ldots seven options left,'' he said.  ``I did plan for this.  This is an \emph{incomplete} shutdown, so we have some freedom to--''



The windows began closing.  Metal shutters.  The apartment was plunged into darkness.  No lights, only the light that slipped through slits in the metal walls.



``This is a \emph{complete} shutdown,'' he revised his statement.  ``Still seven options left.''



``You knew about this, I hope,'' Ingenue commented.



``I \emph{said} I knew about their safety measures,'' Teacher snapped.  ``Not an issue.  I suppose my plan for a surprise shutdown is the clearest at this time.''



``Just what is this working plan of yours?''



``We need to avoid capture for\ldots'' he looked down at his watch.  It had stopped.  ``\ldotsAn indeterminate period of time.  Less than five minutes.  Not an issue.''



``Not an issue?  When we're in the heart of a complex that houses the largest group of heroes from the largest city in the known worlds,'' Ingenue said.



``Not an issue,'' he repeated himself.



``Forgive me if I don't believe you.  I could use my power on you,'' Ingenue said.  ``But I don't even \emph{like} you.''



``I would offer my power, if only to streamline this process,'' Teacher said, ``But anyone acquainted with me tends to misconstrue that as more insult than anything.''



``It implies we're stupid,'' she said.  ``Or desperate.''



``I can see where it might.''



``If we get arrested, we get arrested,'' she said.  She was watching as the ex-viking split off another copy of himself.  ``I'd rather play nice and get moved to a smaller cell than get shot pushing things too far.''



``We're not going to get shot, nor are we going to get arrested.  I \emph{do} pride myself on having plans that \emph{work}.  Any contingency plans are more a matter of flexibility and convenience than a belief that my core plan won't \emph{work}.''



``You sound annoyed.''



``You spend over a decade as a supervillain, put plans in motion, great and small, with a flawless rate of success,'' Teacher said, ``First bump in the road, and you get questioned.''



``You were arrested.''



``I was \emph{between} plans,'' Teacher said.



The viking's clones changed.  One man, one woman, Asian and black in appearance, respectively.  The third began to alter, his flesh swelling and contracting as he took on the form of a larger man.



His original self held out some discs, checking the front and back, then frowned.



``Problem?''



``No power.  If we're fighting, then I'm fighting naked,'' he said.  But even as he said the words, the individuals began sprouting clothes, folding them out of flesh.  The color began changing.



``Against armored foes?''  Teacher asked.



``Probably won't put them down, but I could distract.''



Teacher nodded.



``A shapeshifter,'' Ingenue said.  ``Do I know you by another face?''



``I wasn't in the Birdcage,'' the viking said.  ``Satyr.''



``Charmed.''



\emph{Nymph and satyr}, Teacher thought.  He didn't dwell on the thought.



``The pair are getting closer,'' the woman in white said.



``Good,'' Teacher answered.  ``Come here.''



She did.  He could intensify his power, scale up the strength of the ability with the effect on the subject, but hers was minor at best.  He'd wanted assistance from a \emph{person}, rather than an invalid.  It had been good that her spirit had been broken when he'd found her.  It meant she was more compliant in general, without being useless.



\emph{She's happier now}, he thought.  She had been lost, and now she had direction, even if it was his.



That the precognition was barely set in made it easier to undo.  His awareness touched on countless abilities, arranged in grids and rows in the background of his mind



There were caveats.  Issues.  He could grant a kind of specialty in a particular field, a mastery over a given subject.  \emph{This} was how he found his expert teachers, ironic as it was. It was also how he made his tinkers, pushing that mastery to the point that it went just beyond the normal limits of theory and knowledge.  Doing it with enough people, putting them all on one task, and he was effectively a tinker himself, in a roundabout way.  There were tradeoffs in needing personnel, and a lack of reliability in the end product, if he didn't carefully check every step of the way, but he was a low level tinker in every field.



He could also grant a wealth of mental powers.  Perception powers, powers that gave perspective, or peculiar forms of genius that operated by different rules.



It was \emph{this} type of power that he gave to her.



The D.T. officers drew closer.  They could see through walls, they were strong, tough, and they would win a fight by virtue of the computers they wore.  The suits couldn't be hacked, and there were no convenient weak points to target.



Through his maintained contact, the woman in white changed, her power adjusting.  Clairvoyance.  Seeing everything in a small radius, inside and out.



He finished, then drew a notebook from his robe, handing it to the woman in white.  ``Map.  Mark out people and anything else that wasn't on the blueprint I showed you earlier.''



She set about drawing, her face an inch away from the paper in the dim.



``Sitting in the dark, armored suits converging on us, in the middle of superhero central,'' Ingenue said.  ``I find myself concerned.''



``You said you weren't worried.''



``I'm not worried about \emph{them}.  I'm worried that you're as invested in me as you are.  You expected something along these lines.''



``I did.''



``That means you want me, you want my power, or both.  Badly enough you'd take this risk.''



``The word `risk' implies the outcome is in doubt.''



``The outcome is always in doubt.''



He shook his head.  ``Let me assuage your worries with two words.''



``Two words?''



``Stockholm syndrome.''



``Where a captive falls in love with the captor.  Beauty and the Beast,'' Ingenue said.  ``I always did like the princess movies.''



``I give people power, and I think there is a submissive kind of appeal to being a slave.  To being \emph{numbed}.  Some fall for me like an alcoholic falls to drink.  Love, after a fashion.  In your case, that's almost a defense mechanism.''



``A defense mechanism?  I fall in love with you, you get the benefit of my power\ldots''



``Things don't turn out well for your boyfriends, as a general rule,'' Teacher commented.  ``Psychosis or a kind of obsession.  No.  I'm not aiming to capture you.  That's the \emph{opposite }of what I'm trying to achieve.''



``You're going to need to explain that.''



He smiled a little.  ``In time.  Ready, Satyr?  You remember the plan?''



Satyr nodded.  ``I have a good memory.''



``Let's confront our opponents,'' Teacher said.



Satyr nodded.  His shapeshifted clones led the way.  Teacher lagged behind, picking up the teleportation circle.



They headed straight for the men in armored suits.  Five in total had gathered.  Others were elsewhere in the area.



``Excuse me,'' Teacher spoke.



The men in suits trained weapons on him.  Singling him out in the group.  The clones stepped closer to Teacher, providing a body shield.



``In a matter of minutes, my followers are going to carry out the plan I outlined,'' he said.  ``There are four actions they're going to carry out.  The one you should be \emph{most} worried about is a tractor beam.  It's set up fairly close by, and it's going to fire on this structure, cutting out a cylindrical section and slowly withdrawing it.  I'm sure you've played games as a child, maybe you played that one with the wooden blocks you pull out of a tower.  They're going to withdraw much of this floor.  With it gone, the \emph{upper} floors are going to topple.  Some will land on the building next to us.  I seem to recall there's a small hospital in there.''



``Hands on your head and turn around,'' one of the D.T. officers said.



``The people manning the tractor beam are all ex-heroes.  Capes who came to me in desperation, who couldn't pay, and other innocents.  I wouldn't advise an attack.  I set up measures to ensure it would end badly for everyone involved.''



``\emph{Now}!'' the officer barked.



Teacher turned around, tossing the teleportation circle off to one side before putting his hands on his head.  ``Right now, I know you have ships in the area, positioned to catch our getaway vehicle.  I know exactly how many you have.  With the number of people in this building, you'll need every single one of those suits to evacuate everyone in time.''



A D.T. officer reached out, foaming the pad.



``\emph{Every single one.  }The section of building the tractor beam seizes will be collected by my getaway ship, with me inside it.  After that, the building will collapse.  You could attempt to stop the process, but I can guarantee there would be a cost.''



The D.T. officer tapped one foot against the back of his knee, forcing him to bend it.  He dropped to the ground.  He could hear the clink of chains.  Cuffs.



``The alternative is simple.  I know there are heroes listening in.  Chevalier, maybe, or Legend.  Defiant, perhaps, given how \emph{someone }seemed to be able to work around my hackers?  If you stop jamming my equipment, I'll use that teleportation pad in the corner there, along with my colleagues.  I leave, you don't have to worry about me, and the building stays up.  You can keep the people manning the tractor beam.  My gift to you.''



He waited, feeling the metal cuff encircle one wrist.  The D.T. officer circled around, looming over him.  Black armor, complete with an onboard system.  Ominous.



``Ingenue wants to go, and if you push matters, you're going to have to see us in court, and you'll have to explain the security measures you're enforcing on her.   You'd win, very probably, but it would become public knowledge that you aren't holding to the spirit of the amnesty.  That's strike one.  Strike two?  Losing this building.  This would be a terrible time to have a fixture and a power base crumble.  It would affect the tens of millions who pass through this area or see it from a distance.  You don't want the blow to morale.''



He waited.  The second D.T. officer started working on the others.



Still kneeling, Teacher met the eyes of the D.T. officer standing above him.  The man's eyes weren't visible, but a red light blinked in the corner of one.  Teacher continued, ``Strike three?  Even if you brought me into custody, and there's no guarantee that would succeed, I have other students, elsewhere.  You would be sentencing them to die, if I wasn't there to look after them, to access them where I've tucked them away.  You gain nothing of substance.  Putting me behind bars, fine.  But what does that \emph{get} you?  With the amnesty, the only thing you can charge me with is breaking and entering.  Losing this building, dozens of lives, reputation\ldots merely to stop me?''



``You may be understating your own importance,'' Ingenue murmured.



``Shh,'' he said.  ``I'm making a compelling argument, don't undermine me.''



The D.T. officer spoke.  ``I've been instructed to tell you that we don't negotiate with terrorists.''



``Weigh this mathematically, how many lives are ruined by this one moment of stupidity, compared to the lives you \emph{think} I'd ruin if I continued operating on my own?  Weigh it emotionally\ldots''



The blinking of the red light at the corner of the D.T. officer's mask sped up. Teacher glanced back.  Satyr and Ingenue were caught, hands bound.  The D.T. officer was tying up the clones, now.  Others were watching hallways.



The blinking light turned yellow, then green.  A mist erupted around the pad.  The foam that bound it in place broke down.  It skidded across the floor, propelled by small wheels.



Teacher let himself topple.  His shoulder hit the teleportation pad.  Crackling swept over the length of his body.



His students were waiting as he appeared on the other side, dragging him off.



Ingenue, Satyr, and the woman in white followed, in that order.



It took time for them to get sorted out.  His students milled through the area, scanning them for trackers and other signatures.  Devices were used to scramble the teleporter's signature to prevent anyone from following.



The area was a broad building with a high ceiling, most of it occupied by a single machine.  The best he could do without a Doormaker of his own.  Sixty of his students milled through the area, seeing to their individual tasks.



``How?'' Ingenue asked.



``We did our research,'' Teacher said.  One of his students cut the chain between his cuffs.  ``They had to use the suits.  Protocol when Ingenue is involved.  The ambient shutdown effect doesn't include the suits, because the suits have to operate at one hundred percent when there are capes on the other side.  Once it was close enough to one of them, the crew on \emph{this} end could operate it.''



``If they'd destroyed the pad--''



``Against protocol, again.  You don't shoot tinker devices.  At best you bury them in containment foam, and I used my access to Dragon to find the formula for a counteragent.''



``You can't cover every eventuality,'' Ingenue said.



``My plans \emph{work},'' he said, dusting himself off.



Her voice was hard.  ``If you want my help, fine.  But don't involve me in your lunatic schemes.''



He paused.



Lunacy, madness.



Speaking of\ldots



``Where's our distraction?''



``Lung finished the job ten minutes ago,'' a student answered.



``He found it?  I'll want to see pictures.  I feel like a child on Christmas.''



``Bringing them up right now, sir.''



``No incident?''



``There was an incident,'' the student said.  Blunt, there was no emotion on his face.  No indication of whether it was a continent-destroying error or Lung killing a student.



``Show me.''



Monitors lit up.



Lung was a mercenary hire.  The site was a vault, and fallen capes littered the area.  The view shifted as the camera did, showing a share of Lung's claw.  He was so tall that his hand dangled at what was shoulder level for the students walking alongside him.



The man had refused to let Teacher use his power on him, but he'd agreed to cold, hard cash and a group of Teacher's students joining him to ensure the job was finished.  They were dressed in white outfits, carrying hardware he'd paid a pretty penny for.  All had powers of their own, on top of the complimentary powers he'd granted them.  They were loyal, and they would die if he ordered it.



The scene was almost comical, on a level.  There were warnings plastered everywhere, skulls and crossbones engraved into stone, and even yellow police tape here and there.



Lung ignored it all.  He'd changed, fighting past the defensive line.



Every plan had to involve a win, Teacher mused.  He had a good streak going.  Using Lung, using the man \emph{now}, it meant pulling stronger heroes away.



Either Lung was removed from the big picture, and a chaotic element was dealt with, or Lung succeeded, and Teacher could banish one niggling doubt, sleeping just a bit easier.



He'd done a lot of research, ordering his minions to dig up footage, finding it wherever it was available.  He'd had them search it, then double checked it himself.



But an educated guess was still only a guess.



Lung tore into the last vault, rending the hinges, then slowly peeling it away, heating the metal as he went.



``They didn't send one of the major capes?  Chevalier?  Valkyrie?''



``Too far away, sir.''



Far away meant different things, in this new future.  A world away in another universe was very possible.



``Good fortune for us\ldots or particularly \emph{bad} fortune, if this incident--''



He trailed off as Lung entered the vault itself.  The camera shed light on the contents.



Satyr hung back, arms folded.



``What is it?''  Ingenue asked.



``A quarantine area.  \emph{That} was the weapon the Endbringer was using.''



A gun.  It was dark gray with a faint green speckled coating on it, where one material had been broken down and incorporated into the outer coating.  There was a gouge in the side where a feather had cut the housing, but it was otherwise intact.



Over and over, the Simurgh had protected the weapon.  He'd seen it, had checked the footage, had seen her go out of her way to shield it with her wings.  She'd done it subtly, most of the time, events contriving to make it look more accidental than anything.



She couldn't make tinker devices herself.  She had to copy the designs of tinkers near her.  He'd found who she'd copied, a now deceased cape from Brockton Bay, and he'd found the designs.



There were discrepancies.



He was all too aware that he could be walking into her trap.  He had enough precogs around himself and, in that video, around Lung, that the Simurgh shouldn't have been able to leverage her full power against them, but she could have put things in place, not knowing exactly who, but still knowing it would be bad.



The weapon had been lost in the course of the battle, and the heroes had decided to minimize contact with the thing, locking it away.



``Quiet, please.''



The bustle of his students working around him stopped.



In the silence, he could hear footsteps behind him.  He, Satyr and Ingenue were joined by a third person.



Teacher spoke without turning his head.  ``You've seen this video already, I expect?''



``Yes,'' Contessa answered.



Lung tore into the casing, much as he'd torn through the vault door.



There was a scratch as Lung's claw touched glass.



He tore at the metal, peeling it away while preserving the glass.



There was fluid inside.



The light caught the glass, at first, obscuring the contents.



A baby.  Male.  With large ears and a large round nose.  Not attractive, as babies went.



One or two years old?  Accelerated aging?  Where had the Simurgh been in contact with a tinker with that particular knowledge?  Bonesaw?



That was disquieting enough on its own.  Was the child tinker harboring knowledge?



``These are the big things you were talking about?''  Ingenue asked, her eyes wide.



``Actually, no.  I had suspicions, but the Endbringer making a baby wasn't one of them.''



Lung touched a burning hand to the glass, melting it.  Water steamed on contact with his claw.



``No,'' Teacher said.  Idiotic, considering Lung couldn't hear, and the event had already passed.  Still, he couldn't help but add, ``Don't.''



The water was crimson and boiling by the time Lung withdrew his claw.



The monster turned to leave, the polluted water still popping behind him.



``I'm not sure whether to be relieved or very frightened,'' Satyr commented.



``The\ldots incident?'' Teacher asked.



``Ten minutes from now,'' a student said.  ``He growls a bit, but there isn't anything we can make out.  He was just walking, and our camera follows''



``Skip forward, then.''



The video skipped forward.  Lung was in a dark stairwell, reinforced concrete and steel beams, light above him.



He stepped up onto the surface, his clawed feet sliding where they were too long and wide to fit on one..



The Simurgh was waiting.



Lung was her height, bristling with scales.  She looked more human of the two, pale, her hair blowing a bit in the wind, unreadable.



Monsters, the both of them.



``\emph{Well done},'' Satyr said.  ``You may have killed us all.''



``She \emph{moved}?  She isn't dormant?  Did she attack a target?''



\emph{Did I just start the cycle up again?}



``She returned to orbit.''



Teacher nodded, but as much as experience had inured him to the horrors of the world, he couldn't help but feel a sick knot in his gut.  That didn't mean anything.  Had she gone dormant again, or was she waiting?



Or was she doing something else entirely?



``I don't understand,'' Ingenue said.



\emph{I don't either, }Teacher thought, but he didn't say it out loud.



``She may well try again,'' Contessa said.  ``It's hard to say how, when she isn't involved in things.''



Teacher nodded.



``What will you do?''  Contessa asked.



``If she's going to try again, I'll find out, and I'll take actions to stop it.  I'll have to bring others on board.  Heroes, maybe.  Learn from the mistakes of my predecessor.  Doing the same thing over and over again and expecting different results is insanity, isn't it?''



``There's a saying along those lines,'' Contessa said.



``You said she'd try again.  She'll try \emph{what}?''  Ingenue asked.



``I'll find that out too,'' Teacher said.  ``I wish Lung hadn't destroyed the corpse.  With luck, the heroes won't seal the vault for quarantine's sake and they'll check for DNA.''



``I could find out,'' Contessa said.



``You're going to help?''



She seemed to think for a little while.  ``Most likely.''



With that, she walked off.



More a cat now, walking its own path, than a loyal dog.



Still, she was in his camp.  At least for now.



He nodded.  ``Right.  That was it, with this job?  Anything else?''



``Lung called to leave a message, sir,'' the student said.  ``It was only barely intelligible.  He said you could consider that a breach of contract, if you wished.''



``Pay him.  It leaves the door open for future hires.''



``Yes sir.  And you have a message from Marquis.  He'll accept you any time today.''



``Do you have coordinates?''



``Yes sir.''



``I'm coming, I assume,'' Ingenue said.



Teacher nodded.  As much as he wanted to rest and get his bearings, he had to keep moving.  ``Saint?''



A student in the corner turned.  It took him a second to muster the functions needed to reply.  ``Sir?''



``Dragon's code.  Any changes?  Anything significant?''



Saint slowly shook his head.



``What are you thinking?'' Satyr asked.



He shook his head.  ``A thought.''



Who had beat his team of hackers?  Defiant wasn't \emph{that} good.  Either something had gone wrong with his team, or Dragon was somehow active and hiding that fact from him.



\emph{Paranoia.}



He and Ingenue stepped into the teleporter.



Marquis was sitting on the stairs in front of a sprawling summer home.  A jug of iced tea sat beside him, along with a plate of cookies.



``Iced tea?''  Teacher asked.



``I picked too warm a place to spend the winter,'' Marquis said.  ``Ingenue.  How's the love life?''



She frowned a little.



``Sit?'' Marquis offered, indicating the stairs.



Teacher sat.  It wasn't comfortable, and he wasn't a shapeshifter in any capacity.



``So.  Do we discuss business first or do we conduct meaningless small talk?''



``A few minutes ago, I would have said `business','' Teacher said.  ``But I've had enough business for a time.  Is your family well?''



Marquis stretched a little.  He took a cookie, then offered one to Ingenue.  ``Iced tea?''  Either of you?''



Teacher looked up at the sky.  The sun beat down on them.  ``I'll take you up on that.''



``Please,'' Ingenue said.



Marquis took the time to pour it.  He handed the glasses to the others, then filled his own glass.  ``By the by, if you bring up my daughter again, Teacher, I'll lobotomize you.''



Teacher nodded.  ``Noted.''



``Needle up one nostril, jab the front of the brain, scrape\ldots I digress.  There's no way for you to mention her without it sounding like a threat, so I'd rather you avoid the topic.''



``I can do that,'' Teacher said.



Marquis smiled.  ``Since you already asked, though, she's saying goodbye to her family.''



``What does that mean?''



``It means what it means.  Putting bad things to rest.  Moving on to, well\ldots bad things.  But in a good way, I hope.''



``I presume you're the bad things she has in the future.  You're continuing your career, then?''  Teacher asked.



``Could \emph{you} stop?''



``No, but I'm tied up in the business, and  I never really stepped away from it.  I'd wondered if you could, having had some time away.''



``I was cell block leader.  Hardly a vacation from supervillainy.''



``But you've left your old business partners behind, there wasn't anything to return to, after eleven years in the `cage.''



``I went back to it right away,'' Ingenue said, quiet.  ``It's surprisingly lonely.''



``Raises the question,'' Marquis said.  ``Can a person change?  I suppose if I was going to, my daughter would be a reason.  My job took her from me in the beginning, after all.''



``But you're going back?''



``Call it narcissism.  I love `Marquis' too much to say goodbye to him.''



``The original Narcissus loved himself so much he withered away,'' Teacher said.  ``It can be a kind of personality disorder.  A kind of madness.''



``An odd tangent,'' Marquis observed.



``Isn't it?  I've been focused on the big picture for some time, and I found myself in the position as one of the most powerful villains.  My plans came to fruition.  I have what I want.  I'm looking at things on a different level.  Where do we stand?''



``Humanity as a whole, or us, as individuals?''



``Both?''  Teacher asked.



``You've been dwelling on the subject.  Tell me your thoughts, first.''



``You asked if a person could change.  I look at us, at the people we interact with, and I see madmen and monsters.  Is that just \emph{us}, the individuals, or is it mankind?  I could use my power, set a team on it, find out, but I'm not sure I'd like the answer.  I'd \emph{like} to change, and that's a heck of a lot easier, because I can lie to myself, whatever the outcome.''



``Which leads, I presume, to your business deal.''



``Capes.  The theory going around, after the revelations about Scion, involved all powers being parts of a whole.  We've seen how some powers are devastating in concert.  It was, after all, how we won, on a level.''



``More or less true,'' Marquis said.



``I've achieved all I wanted to achieve.  I sell powers, I have wealth, I have a small army at my disposal.  I have enemies, and in an odd way, that's something I wanted too, because it keeps life interesting.  But I feel a need to strive for something higher.  Can we put the \emph{whole }back together?  At least in part?''



``This is why you wanted me to come,'' Ingenue said.



``Everyone wants something.  I think, with the right people, the right combinations, and unity, we can achieve what we desire most.  An alliance, not for villainous purposes, but to achieve something greater.  Fighting against entropy and all that is wrong in the world.  Satyr is on board, but he wants a great deal.  I don't think I need to ask if there's something \emph{you} want, Ingenue.''



``No,'' she said, looking momentarily distracted.  She looked up, ``But I don't see how this helps.''



``We habitually seek out money and prestige,'' Teacher said.  ``Why?  Because it's power, in an abstract way, and you need power to change the world.  I think we can achieve power in a more direct manner.  There's a trend at work, parahumans taking positions of power.  What if we take it a step further?  Forget money and position.  Everyone in our group gets what they desire most, we enforce a kind of cooperation, a joining or sharing of powers.  We put ourselves above even governments and warlords.''



``Everyone gets what they want most,'' Marquis mused.  ``I can't think of anything more terrifying.  If I back out, will you be plotting to murder me?''



``No.  But I would prefer you didn't go talking about this.''



``I'm to remain silent while you build your secret society and start tampering with things that should be left alone?''



``Call it professional courtesy?''



``On the topic of courtesy, something tells me you're after my daughter, for this group of yours.''



``Your daughter \emph{is} an adult.  Capable of making her own decisions.  I was going to bring her up later.''



``You're not winning me over, Teacher.''



``I'll make you a deal.  Let me make the offer to her.  She accepts or refuses it herself.  If she says no, I leave it be and find someone else.  Either way, you respect things with your silence.  I won't take any action against you, but I can't promise my partners will be so polite.''



``Mmm.  A counteroffer.  \emph{I} make the offer, as you outlined it here, and she decides from that.''



Teacher nodded.



``Power and control,'' Marquis said.  He sighed, then bit into a cookie.



``You can't avoid it,''  Ingenue asked.  ``Can you live without charm, intimidation, or some form of influence over others?  Without making others do your bidding on some level?  You flirt, they react one way or another.  \emph{Everything} is manipulation.''



``I think there's such a thing as extremes,'' Marquis said.  ``Case in point\ldots''



``I think I know who you're thinking of,'' Teacher said.



``She had it all, and see where it got her,'' Marquis said.  ``A lesson for you, Teacher.''



It was enough to give Teacher a moment's pause.





