





The train jerked into motion, and the men and women in the aisle stumbled.  There was a crowd at the front, where an old woman had taken a while to handle her fare.  Even now, she made her way down the aisle with excruciating slowness.  The people behind her looked irritated enough to snap.



``Hey.  Miss?''



The old woman stopped, glancing down.  The seat was occupied by an older teenager, bundled up in an overcoat and scarf, with a wool cap pulled down over close-cropped light brown hair.



``Take a seat?''



``Oh, that's alright.  I prefer window seats.  I think there's one open at the back there.''



``Take my seat.''



``I couldn't do that.  I--''



But the teenager was out of the chair, swiftly vacating the spot.  With a peculiar awkward slowness, the teenager picked up the backpack and moved out into the aisle, leaving the way clear.



``If you insist.  Thank you,'' the old woman said.  She took a few seconds to get settled.



With the woman out of the way, the people in the aisle were clear to move on.  The teenager ignored the grateful looks and glances from the ones who'd been stuck behind her.



``You aren't warm in that jacket?'' the woman asked.



``I was cold when I got on.  By the time I warmed up, I was close enough to my stop that I figured it would be silly to take it off and then put it back on.''



``I see.  Fair enough.  Are you traveling for business or pleasure?'' the old woman asked.



The teenager struggled to move the heavy backpack to the floor.  It slid from one knee, and the old woman reached out to help catch it.



They worked together to lower it to the floor.



``Is that alright?'' the older woman asked.



``Yes.  Thank you.''



``A heavy burden, that.''



``It's not too bad.''



The woman frowned, peering, ``You're breathing a little hard.  Are you okay?''



``Yeah.  No worries.''



The last of the passengers settled in the train.  The teenager and old woman both watched out of the window as the landscape passed by.  Rural areas, farms, fields dusted in snow that didn't quite cover the grass, the occasional horse or cow searching for something to eat.



The train reached a bridge.  The landscape zipped by and was replaced by water.  Snowfall obscured vision beyond a few hundred feet away.



``If I was bothering you with the questions, let me know,'' the old woman said.



``You're not bothering me.''



``You didn't answer my question earlier.  Business or pleasure?''



``Everything's pleasure, I think.''



``Well \emph{that}\emph{`s }good.  When you find what you really \emph{enjoy} doing, I think you find that business \emph{becomes} pleasure.''



``That's very true.  You?  Business or pleasure?''



``Bittersweet pleasure.  I'm visiting an old friend.  We went our separate ways,'' the old woman confided.  ``I admit, it was probably my fault.  I wasn't considerate.''



``No?''



``Maybe it's better to say I was prejudiced.  She confided in me and I betrayed that trust.  A different era, but that's a poor excuse.  As a friend, she deserved more than a knee-jerk reaction and disgust on my part.  I've been graced with a chance to redeem myself, and I'm going to go to dinner with her and her partner and we're going to have a merry time of it.''



``That's excellent.  Can I ask?  Is she gay?''



``She's white, he's black.  I know, I know, it sounds bad, but I consider it a kind of penance, freely admitting I was a smaller person back then.  I let others dictate how I should feel, instead of considering her as a friend and looking at things objectively.''



``It's big of you to admit that.''



``When you reach the end of your life, you have a chance to take stock.  You sum it up, and you decide if you want to spend your remaining years, months or days in regret or satisfaction.  My late husband told me that.''



``Was he a psychology professor?''



``Sociology.''



``That's from Erikson's work, the last of the psychosocial stages,'' the teenager said.



``A college man.  I'm impressed.''  The old woman's voice was quiet, oddly respectful of other passengers, in comparison to her dawdling earlier.



The teenager smiled.  ``I read up on stuff.''



``It took me a \emph{while} to wise up.  It was only after my husband passed that I looked back and started taking stock.  If there's any point to what I'm saying, it's that there were a lot of ugly feelings about skin color, back in the day.  But we get better.  There are similar feelings about the gays, but we're getting better about that.  Less wars than there were in the past, whatever the news would tell you.  People are happier as a whole.''



``I wonder sometimes.''



``It gets better,'' the old woman said.  ``Really truly.  We have our low points, I won't deny that, but it gets better.''



``I don't want to sound negative, but, um, I guess I'm going to sound negative.  There are people in third world countries who might disagree, and victims of Gold Morning.''



``Even there, on the whole, things are steadily getting better.  I promise.  Don't get me wrong, bad things have happened.  People die, and a lot died horribly.  My sympathies are with everyone who was or is touched by any of that.  But \emph{on the whole}, it looks worse than it is, with the worst of it constantly on the telly.  It's easy to get too focused on our individual problems and lose sight of the big picture.  The big picture is promising, I think.''



``Huh.''



``But it's worth saying that it's up to \emph{people} to make it better,'' the woman said.  ``I trust that \emph{people} will improve, as a group, but we can help it along by striving to be better people on an individual basis.''



``That makes a lot of sense.  I'm not sure I totally believe it, but it makes sense.''



The old woman leaned in close, conspiratorially. ``With all of that said, in the interest of being better individuals, I'm going to have to ask you a question.''



``A question?''



The old woman she didn't maintain eye contact, and she wasn't smiling.  ``This is me, being brave and trying to be better like that.  And if I'm wrong, well, I'm hoping you'll continue to be the gentleman you've proven to be and not fuss over an old idiot's ramblings.''



``I'll try,'' her seatmate said, smiling a little.



``I just need to know\ldots is that backpack of yours holding something dangerous?''



``Dangerous?''  The smile disappeared.



``A \emph{bomb}?'' the old lady whispered the question.



The response was a stunned series of blinks.  The teenager had to bend over to get at the straps and clips before opening the bag.  Clothing had been rolled up and piled inside.  The clothing was moved to reveal more contents from inside the bag.  A bag with the end of a toothbrush sticking out, a laptop.



``If it is, it's a pretty awful one.''



The old woman had the grace to look embarrassed.  ``You must think I'm crazy.''



``Something seemed off, you asked.  No, I don't think you're crazy.''



A ding sounded, before the announcement sounded throughout the train.  ``\emph{The train will be arriving in Philadelphia in five minutes.  Please gather your belongings and collect your litter from your seating area}.''



``That's you?'' the old woman asked.



``My stop, yeah.''



``You have a good day ahead of you, I hope?''



``I hope.  A meeting.''



``You're doing the same thing as me, then.  A reunion.''



``Of sorts,'' The teenager said, slinging the backpack over one shoulder.  ``Thank you for the talk.''



\sectionbreak



Tattletale allowed herself one last check of her computer screens.  There were brief, coded messages from various minions and soldiers, from spies and informants.  The tail end of those windows had responses from Imp and Parian.



Video footage showed a replay of Lung's fighting retreat from an area in downtown New York B.  There was footage of the PRT base, Valkyrie standing off to the side, trying to look far less interested than she was as a young man tried on a white bodysuit.  One window showed the various Endbringers, all of them motionless, but for the Simurgh, who was airborne.  The last of the original three.



One of the windows updated.  A text message from Imp.



Imp:I've been waiting for five minutes.



Tattletale hit a few keys.  Nobody waiting was outside.  She typed out a response on her phone.



Tattletale:
waiting?



``Seriously,'' Imp said, from right next to her, her chin resting on Tattletale's shoulder.  Tattletale jumped a little, despite herself.  ``Five minutes, and you don't look at porn \emph{once}?''



``One of these days, you're going to give someone a heart attack.''



Imp put away her phone.  ``I've killed before.  He was a clone, but I still offed him.''



``Let's \emph{not} make murder a rite of passage.  Too many new bodies in our ranks, we have a tone to set,'' Tattletale said.  She hit a key combination and locked the system.  Another key turned off the monitors.  The three-by-two arrangement of screens went black, the outermost one first.



``New bodies?  Beyond our individual teams?  My Heartbroken, The Sons of Bitch, the Needlepoints?''



``Needlepoints?'' Tattletale asked, arching an eyebrow.



``If they're not naming themselves, I'm gonna name them.  Or do you want Parian's group to wind up with a bullshit name like `Faultline's Crew'?''



``Noble of you to spare them that,'' Tattletale said.  She rubbed at her eyes.



``You're usually on to me.''



``I'm usually a little sharper.  I only connect dots from whatever info I already have, and when I'm this focused, I don't have much.''



``Big bad villainess, staring at a computer screen all day,'' Imp said.  She sat down in Tattletale's chair.



``Too much to keep track of,'' Tattletale said.  She opened a fridge to grab a fat green bottle and a sixpack of assorted sodas.  ``I'd plug myself into the internet if I could, take it all in while I go out to see the \emph{real} world.''



``Sure, yeah,'' Imp said.  She fished in the cupboards and found plastic-wrapped chocolate cupcakes.  ``Fuck \emph{yes!  }I didn't think they made those anymore.''



``They don't.  I think those go for sixty-four dollars a package, nowadays.''



``Mm,'' Imp said, through a mouthful of one cupcake, covering her mouth as she spoke.  She had her eyes closed in ecstasy.  ``Tashdy fuggin' siggy-foh dowwuhs.''



Tattletale set the bottle and the sixpack down on the table in the center of the meeting room, then collapsed into a leather chair with a high back.  She resisted the urge to reach for the nearest laptop, instead draping one arm over her eyes, reclining.  ``You didn't have any trouble getting here?''



``Nuh uh.''



``I suppose you wouldn't.  Where are the Heartbroken?''



``I brought four,'' Imp said.  She licked her thumb, then rubbed at one corner of her mouth.  ``Downstairs.  I ordered your soldiers to look after them and make sure they were being good.''



``That's uncharacteristically unkind of you,'' Tattletale said, without moving her arm.



``Oh, sure, I can leave little dolls all over someone's place, in less and less obvious places, until they snap, I can steal someone's pants every time they go to the bathroom, I can even, on occasions that warrant something above and beyond, use a knife on someone and leave them wondering what's happening to them as they bleed.  But I ask some soldiers to babysit some orphans, and oh, \emph{now} I'm little miss evilpants.''



``Are you going to call them off, or do I need to call the security team and let 'em know?''



``I'm trying to set you up for a whole humorous interplay here, like, you look at me all stern and I do the `oh, right, that \emph{is} worse' thing.''



``You didn't answer my question.''



``I'll fricking call them, you wet blanket,'' Imp said.



There was a knock at the door.



``And get the door,'' Tattletale added.



Imp grumbled, but she made her way to the door, her phone in one hand.  She was still looking down at her phone as she opened the door, then turned wordlessly to make her way back to the kitchen.



``A glowing welcome,'' Foil commented.  ``I can't imagine why it's been so long since we crossed paths.''



``Imp is pouting.  Ignore her.''



``Har har,'' Imp said.  She tossed her phone onto the table.  ``There.  They should be good now.''



``They?  Heartbreaker's kids?''  Parian asked.



``I call them the brats, but sure.  We can go with that, for clarity's sake.''



``Cute kids.  They were whispering and giggling with each other when we passed by.''



``Oh mannn,'' Imp drew out the word.  She paused, hesitating, then groaned.  ``I'll be back.''



Imp skipped out of her seat, then ran to the hallway.



Foil took a spot on a short couch that sat to one side of the table.  Other chairs were arranged around the thing.  Parian hopped up, then sat on the back of the couch, leaning forward until her chin was on top of Foil's head.  Her arms draped over Foil's shoulders, sticking out more than they draped.



Foil batted at one of Parian's hands, making it swing back and forth for a second.



Tattletale dropped her arm from its position over her eyes.  ``Food went through okay?''



``Supplies were good and timely.  Thanks for the hook up,'' Parian said, moving only her head.



``No prob.  Was the data good on Carver and his gang?  I was using a new source, so \emph{any }complaints would make a world of difference.''



``It was perfect,'' Parian said.  ``We dealt with him, and it's all been quiet.  I feel bad for thinking it, like I'm violating the sanctity of it all, but I can't help but wonder if things are legitimately \emph{cool} or if this is just the calm before the storm.''



Tattletale said, ``That's kind of why I called you guys here.  But there's no point dwelling on it before the others arrive.  Can I grab you something?''



The pair shook their heads.



``Right.  As far as the peace and quiet go, take advantage of it while we have it.  Rogue thing is going okay?''



``I dunno if you can call it rogue stuff.  It's more like what we were doing in the bay, but with some legit business on the side.''



``Legit business you're paying for with less legitimate money,'' Foil said.



``I didn't say I \emph{liked} how it turned out.''



``But you accept it,'' Foil said.



``I accept it,'' Parian said.



Foil nodded, as if satisfied.



``Can I ask how your friends and family are doing?''



``You can ask, but I dunno if I have much to tell you.  Better, but not as good as it could be?  Best surgeon in the world changes their faces and bodies, it's a hell of a project to get things changed back.  Especially when a good share of the surgeons out there are dead.''



``I could put you in contact with Panacea.  I don't know what she's doing, really, but I know that Bonesaw wouldn't go over well, and Panacea might help out in her place.''



``Lily already tried, talking to some people she knew from before.''



Tattletale sighed.  ``Damn.  Want me to pull strings?''



``Sure.  Please, If you could.''



Tattletale nodded.



``You're being \emph{nice}.  What's the deal?'' Foil asked.  ``You're buttering us up.''



``Two years in the company of evil, and you still can't give any of us bad guys the benefit of a doubt?''



``I can give \emph{lots} of bad guys the benefit of a doubt,'' Foil angled her head slightly upward, her eyes moving up to where Parian was resting her head.



``She doesn't count,'' Tattletale said.



``Even others.  But \emph{you}\ldots well, I wonder sometimes.''



Tattletale moved her chair back a bit, propping one foot on the table's edge.  ``Accepting my offers for help with one hand, keep the other hand clenched in a fist in case I do something you don't like?''



``Let's not fight,'' Parian said.  She sat straighter, moving her hands until they rested on Foil's shoulders.  ``Not today.''



``Can we compromise?'' Foil asked.  ``Accept that maybe you need a skeptic in your company?  Someone to watch you and call you on bullshit manipulation?''



``If we can even call that a compromise,'' Tattletale said.  ``Sure.  Whatever.''



``Changing the subject to something more pleasant,'' Parian said.  ``I need cloth, if I'm going to keep making designs.  Will you connect me, and how much are you going to want?''



``I can, up to a point, and I want four percent on any profits.''



``Four?  That's more generous than your usual.''



``Four, but fold that in, I want to buy the product, using--''



The door opened.  Rachel loomed in the doorway.



``Hey, mighty hunter,'' Tattletale said.



``Hey,'' Rachel said.  She glanced around, then entered the room, snapping her fingers to call Bastard.



``Managing the first winter okay?''



``Managing.''



``You know you can send an email or make a phone call, keep in touch some.''



``Didn't have power to recharge stuff,'' Rachel said.  ``No gas for the machine, couldn't be bothered to go get gas.  Having quiet and darkness is nice, some nights.''



``\emph{True}, but what if there's an emergency?''



``I can handle most emergencies.''



``And the ones you can't?''



``For those, I have gas, now.''



Tattletale sighed.  ``You're good, then?  Or do you want scheduled gas deliveries, so you don't run out?''



``Sure.''



Tattletale nodded.



Rachel settled into a seat opposite Foil and Parian, Bastard sitting to her left.  She scratched the wolf's head, apparently content with silence.



There wasn't enough time for the silence to get awkward.  Imp returned, and she had Forrest, Charlotte and Sierra in tow.  A little boy rode on Forrest's shoulders.



``I've brought testosterone!'' Imp announced.



``Chairs,'' Tattletale said.  ``Take them.  There's an abundance.  We're just about set.''



Slowly, the others found their seats.  Forrest to led Aidan to a pair of seats next to Rachel, putting himself between the child and the wolf.  The little boy cradled a bird, and a chirp got Bastard's attention, the wolf's head and ears perking up.  Rachel quieted him with an order, and Bastard reluctantly lowered his head to the floor.



``We had to bring some, couldn't do the babysitter thing.  Our kids are playing with the others in the lobby,'' Forrest said.



``Which translates to `let's not dawdle \emph{too} much','' Imp added.



``Two more,'' Tattletale said.



A knock at the door marked another arrival.  Imp had left it open, so she was free to step inside.



Cozen eyed the room.  The thief folded her arms.  She'd adopted a form-fitting jacket with a mink collar, her ample cleavage covered by the length of an overlong scarf.  ``I feel out of place.''



``You were invited,'' Tattletale said.  ``Sit.''



Cozen made her way to the table.  She stepped up to the seat next to Imp, but Imp reached out and put a poorly made doll in the chair.  ``Taken.''



``I travel for three hours to come here, and you won't give me a chair?''



``\emph{I} didn't invite you,'' Imp said.  ``And for reals, this isn't me being a jerk.  Or it \emph{is} me being a jerk, but that's not the big thing here.  This is about symbolism and shit.''



``Symbolism and shit,'' Cozen said, sounding unimpressed.



``Language,'' Charlotte admonished them.  She subtly indicated Aidan.



``I've heard worse words,'' Aidan said, quiet.  ``When Tattletale's giving me lessons and she has to take a call, she has the soldiers watch me, and they know \emph{lots} of bad words.''



Charlotte glared at Tattletale.



Tattletale offered an apologetic half-smile, ``I'll quiz the young sir on \emph{who} has been swearing around him, and heads will roll.  Until then, let's get back on topic.''



``Symbolism and stuff,'' Imp said.  ``There's \emph{lots} of seats, Cozy.''



``\emph{Cozy}?''



``No fighting,'' Tattletale said.  She sighed.  ``Listen, this whole thing is really simple.  Let's do this right, Undersiders stick around, I say what I need to say on other business, five or ten minutes at most, and we're done.''



Cozen frowned, but she circled the table and found an empty chair by the far end of the couch.



The last person to arrive entered without fanfare.  The door clicked shut, and she walked with a quiet assurance to the nearest available seat, which happened to be the one opposite Tattletale.



``You made the trip okay?'' Tattletale asked.



``I did,'' Dinah responded.  ``I saved some questions for the day, but I didn't need them to navigate.''



``Then,'' Tattletale said, gesturing toward the center of the table, ``Forrest, would you do the honors?''



Forrest stood, taking hold of the wine bottle Tattletale had brought out of the fridge.  He removed the cork.



``Temperature should be perfect, I think I timed it right,'' Tattletale said.  ``Oh, forgot the glasses.  One second.''



It only took a minute for the setup to finish, the red wine poured and glasses distributed.  Imp and Dinah received wine glasses of soda.  Tattletale glanced at Aidan.  ``Will he have wine or soda?''



``Soda,'' Forrest said.



By the time Tattletale reached her seat again, everyone was standing, ready.



``A toast,'' she said.  ``I had to think for a good while, to decide what fit.''



``Oh man, is this shit going to be pretentious?'' Imp asked.



Tattletale gave Imp the evil eye as she continued, ``In honor of everything and everyone we fought for and saved.  In remembrance of everything we couldn't save.''



The words hung in the air for a moment.



``Works,'' Imp conceded.



Glasses clinked.  Rachel had a grim frown on her face, mingled with a trace of confusion as she brought the glass in the direction of her mouth twice, before discovering there were more wine glasses to touch hers to.  She seemed relieved when she could finally down the contents and thunk the glass down on the table.



``And,'' Tattletale said, ``Worthy of special mention, entirely separate from the ones we just toasted, because I don't give a fuck about my floors, and because I'm not going to fucking get in an argument about whether we saved them or doomed them, I'm going to suggest a libation for those who have passed from this world.''



``Libation?'' Charlotte asked.



``Yeah,'' Cozen spoke.  Without looking, she turned and poured a thin stream of her wine onto the floor to her left.  ``An offering.  It's why I'm here, since I was with him the most towards the end.''



Tattletale looked at the empty seat beside Cozen.  She'd guessed the number of guests right.  Just the right number of empty chairs.



She could only hope that Taylor hadn't caught on, that in her final moments, she hadn't found out about everyone she'd \emph{really} lost, that Grue hadn't made it off the oil rig.



A white lie for a friend.  Taylor would have blamed herself, maybe rightly, maybe not.



``I like to think it's a kind of payment, more than an offering,'' Imp said.  She shifted her chair a bit, then poured wine onto the carpet to her right, just in front of the crude doll with the white mask and silver crown that she'd placed in the chair.  ``You're missed, dude.''



``I'm glad we could do this,'' Tattletale said.  ``We've been through too much shit together, and I was having trouble keeping us networked.  I thought we needed to touch base.  A little bit of ritual to remind us of the important bits.''



That said, she held a glass out to her left, and she poured a splash out onto the carpet in front of the empty seat in the corner.



Despite her best efforts, Tattletale couldn't help but meet Dinah's eyes.



\sectionbreak



The teenager entered the mall.  People were thick in the space, flowing in and out of a food court with a high-end veneer.  Spinach pizzas were on display alongside a window displaying a wealth of cuts of meat for sandwiches a step above the norm.



Once free of the chill of winter and the periodic blasts of cold from the mall entrance, the teenager pulled off both hat and scarf and undid the large buttons on the jacket.



The old woman had commented on how the world was getting better.  Hard to believe, but it was a nice thought.  It was nice, even, that someone \emph{could} believe it.  The heavy clothing had been a sort of protection against the world, both against \emph{people }and against the world itself.  The protection felt just a \emph{fraction} less necessary than it had before the discussion.



Navigating the mall was easy enough.  It was in the midst of an area with fancy high rises and major law firms, and everything here seemed to reflect that.  Even the people.



A brief feeling of trepidation.



That feeling reached a climax as the teenager came to a stop.



There, just around a corner, there was a point where a coffee shop sat opposite a small multilingual bookstore.  A woman sat at one table outside the coffee shop, a bag placed beside her.  Willowy, taller than the average man, she wore a high end dress suit, and her dark curls were long.  She had a wide mouth that quirked a little as she read something, and her eyelashes were long enough that she looked like she was asleep, sitting there with one leg crossed over the other, her head lowered as she read the open book that rested on the table in front of her, one hand resting on a steaming paper cup.



The teenager surveyed the area, wary, looking for threats and surprises.



Nothing.



No traps, at a glance.



\emph{Easy}.



\emph{This is easy.  Do it}.



One foot in front of the other.



A rising sense of anxiety.



The teenager paused a short distance away, almost paralyzed at the \emph{idea} the woman would look up.



And then what?



Three more steps.  Still, the woman didn't look up.



The teenager placed two hands on the back of a chair, just beside the woman.



``May I?''



The woman glanced up, and the teenager tensed.



Only a glance.  Her eyes returned to the book.  ``Take it.  I'm not expecting anyone.''



\emph{She thinks I want the chair}.



``I meant\ldots is it okay if I sit?''



Another glance, confusion.



``Are you a former client, or--''



``No.  I'm not.''



``I'm afraid I don't understand.  If this is random conversation, or solicitation for something religious, then I'll respectfully decline.  I only get an hour and twenty minutes for lunch, and I'd like to spend it quietly.  Please.''



``I know, I mean, I know about the way you read most lunches, or you go across the street to the museum and wander by yourself with headphones in.  The private inves\ldots''



The teenager trailed off.



``\emph{Private investigator}?''



``I'm doing this wrong.''



``Just a little,'' the woman said.



The teenager sat, then shrugged off the backpack, letting it drop to the floor.  ``I- I'm your daughter.''



The woman frowned.  Her eyes moved to the nearest exit, then to nearby tables and the barista inside the coffee shop.  Checking for a way out.



``I\ldots I know that sounds a little crazy.''



``I'm your \emph{mother}?''



``You're my mom, but you aren't my mother.''



``I have two boys, and I'm pretty sure they aren't\ldots however old you are.  So you weren't switched at birth.''



The teenager took in a deep breath.  ``I'm from Earth Bet.  My name is Taylor Hebert, and my mother was Annette Rose Hebert.  Anne-Rose.''



Taylor watched with bated breath as Annette took that in.  The realization and connecting of the dots was quick enough.  Annette's hand moved, and she lost her page.



``Oh,'' Annette said.  ``Wow.  Wow.''



``If this is too much, or if it's inconvenient or awkward, just say so.''



``But they sealed this world off.  Someone on the other side, they used a device to close all of the doorways, because it looked like there was going to be rioting or war, with too many refugees wanting in.''



``I know,'' Taylor said.  \emph{Except the device wasn't on the other side}.  ``Yeah.  But they sent back everyone that belonged here, and a few of us slipped through before the doors closed.''



``Oh.  Sometimes I've idly wondered, `\emph{what if }\emph{I met the other me'}, but you don't really think it's going to happen.''



``I know.  You should know, just so I can give context to this whole thing, the other you is dead.  She has been for six and a half years.  A car accident.''



``My condolences,''  Annette said.  ``I\ldots it feels wrong to give condolences for my death.''



Taylor smiled just a little.  ``I think it's allowed, to feel weird about this.  I just, um, forgive me for being selfish, but I kind of wanted to see your face.  Or \emph{her }face.''



Annette nodded.  She exhaled slowly, almost but not quite whistling.



``If you want me to go, I'm gone.  Your life returns to normal.''



``I don't want you to go,'' Annette said, her voice quiet.  ``But I don't think it's fair, doing it like this.  I want you to stay because I'm curious, while you have a very real, very \emph{profound} attachment to me\ldots to the \emph{other} me.  I'm worried I'll hurt you.''



Taylor nodded.  ``I can live with that.  Don't worry about me too much.  I'm tougher than I look.  I'm willing to satisfy your curiosity, answer any questions.''



``You're\ldots?''



Taylor took a stab at answering the question.  ``Taylor.  Eighteen.''



``I would have been in college.''



``You were.  She was.  She met a magnificent dorky guy with a warm heart and an awful lot of passion.  He worshiped her, and she\ldots I think he gave her permission to do what she really wanted to do in life, at a time when her parents were being controlling.  Her mother never really forgave my dad for luring you off the track she'd set for him, getting you pregnant with me so early in life.''



``And my dad?''



``Gramp liked him, but not enough to admit it to Gram.''



``Oh.  \emph{My} mother refused to let my children call her Gram.''



``I think my mom and dad encouraged it with me as a kind of subtle payback.''



Annette smiled.  ``What did she end up doing?''



``Teaching.  She was a professor at a University, teaching English.''



Annette's eyes moved to the books, but when she responded, it was a negation.  ``I can't really see that, I'm afraid.''



Taylor nodded.



``Your father?''



``He came over to this earth with me.  He's picking me up in a short bit, we're staying at a hotel for a bit while he does some job interviews, and then we go back to Boston if he doesn't have any luck.  I brought up the subject, and he said he didn't want to see you.  He might try to sneak a peek when he picks me up, if the opportunity arises, but losing her broke him.  He and I, we're both mending a bit, on a lot of levels.''



Annette nodded.  ``Some news from over there made it over here\ldots it's impossible to believe.  We took some damage, but it was comparatively \emph{minor}.  If you can call a death toll of five hundred million minor.''



``No, it was comparatively minor,'' Taylor agreed.



``I'm\ldots I admit, I'm finding myself more and more lost for words, as my curiosity is sated.  I feel like I should say something meaningful, so you didn't spend all this time trying to find some woman without anything to say.  It would be easier if I knew what you wanted.  It makes it hard to tailor my response.''



``I'm not expecting anything profound or special,'' Taylor said.  ``I thought I'd visit, refresh myself on what she looked like.  I\ldots I'm sort of in the same boat as you.  There's a lot I want to say and explain, when it comes to \emph{me}, I want to raise ideas that have been crossing my mind lately, but I'd have to tell a really long story before I could even begin, and I'm not sure I'm brave enough to tell that story.''



``Do you want to try?''



``Telling the story?''



``Or raising the ideas.''



``A lot happened.  My mom died, I had a hell of a time with high school, I fell in with a bad crowd and my dad and I parted ways.  Over and over again, I'd think back to the advice my mom gave me, for a compass, or for a way to frame it all.  Don't- Don't worry.  I'm not expecting that kind of thing from you, I don't want to put you on the spot.  Thing is, now it's all over, and before I came here, someone asked me to make a choice.''



``A choice?''



``Life and death.  Or so I thought.  I chose death, and she gave me life, and I'm still trying to reconcile \emph{why}.''



``I'm not sure I understand.  Does this have something to do with,'' Annette waggled her fingers, ``Powers?''



``No.  It's about regret, and coming to terms with it all.''



``You're only eighteen.  Why are you worrying about something like that at this stage?''



``Because I'm \emph{done}.  My life is \emph{over, }for all intents and purposes.  No matter how hard I try from here on out, I'll never do anything one \emph{ten}–\emph{thousandth} as important as what I was doing \emph{before}.''



Taylor could see people had noticed the emotion in her voice, the slight escalation in volume, and made a deliberate attempt to calm down.



``I might have to hear the whole story before I could give you an answer,'' Annette said, her voice as calm as Taylor's wasn't, ``But I think a lot of people go through near death experiences and I'm pretty sure they feel something like you're feeling.''



``Ever since y- since my mom died, it's been this constant, unending struggle to find some kind of peace, and the harder I tried, the further it went out of my reach.  And now- now I'm \emph{here} and it's right \emph{there}, waiting for me to take it and I can't bring myself to.''



``Because you can't bring yourself to come to terms with whatever decision you made?''



``It's been six months\emph{.  Fuck}, you're just a stranger, and I'm burdening you with this shit you don't understand.  I don't- I--''



Taylor stopped, choking on the lump in her throat.



Annette stood from her chair.  ``Come on.''



Taylor shook her head.  People were looking.  She stared down at the table, and the upside-down book cover.  ``Y- you should go.  I- I picked this spot because I knew you'd be leaving to go back to work, didn't wanna keep you too long.''



Annette reached down, taking hold of Taylor's wrists, where she'd jammed her hands in her pockets.  She stopped short as one hand came free and clunked against the side of the chair, limp and dangling.



``Hav- haven't gotten used to it. Had a better one,'' Taylor mumbled.  ``Before.  Embarrassed `self on the train.  Nearly dropping my bag on some lady's foot because I used the wrong arm, hurt.''



Avoiding looking at Annette, self-conscious, she used her left hand to try and jam the artificial arm into her jacket pocket, failed, and then partially stood, to get a better angle.



Annette took advantage of the movement to fold Taylor into a hug.  Taylor stiffened.



``I think,'' Annette said, ``You have plenty of time to find that peace you were talking about.''



Taylor didn't move, with her face mashed into Annette's shoulder.



For just a moment, she could let herself \emph{pretend}.



For a moment, she was eight years in the past, and all was well, even the evils and disasters of the world were fringe things.  Endbringers in other countries, bad guys who she never had to pay attention to.



``I don't know what happened,'' Annette murmured.  ``I'm almost afraid to ask.  But I don't think you can let one decision you made in a time of stress cause you so much grief.''



``Thousand decisions,'' Taylor mumbled.



``What?''



``It's not the one decision.  It's all of them, pressing down on me.  I'm- I was a monster, Annette.''



``Looking at you right now, I find that hard to believe.''



It wasn't the right answer.  It didn't make Taylor feel better.  Just the opposite.



``And your dad, if he's with you now, he clearly doesn't think that either,'' she whispered.  ``I think I see him.  He looks very awkward and out of place, and he's trying very hard to look like he's not paying attention.''



``That'd be him,'' Taylor said.



She pulled back, but she kept her hands on Taylor's shoulders.  ``If you want to stay, that's fine.  If you want to go, that's fine too.  I wish I had better answers.  My boys are only seven and nine; the hardest question I have to answer is why they can't have pie for breakfast.''



``Be easier to give answers if I could articulate the question better,'' Taylor said.



``I think it was pretty clear.  You said they offered you a choice, you picked death, and they gave you life.  You were talking about wanting peace\ldots I think you had that peace in your grasp.  Am I close?''



Was she?  Taylor nodded slowly.  When she spoke, she could barely understand herself.  ``It shouldn't be this easy.''



``If you don't mind my saying so,'' Annette said, ``I don't think this looks easy at all.  Going down any road labeled `death' has to be the easier road.''



Taylor went very quiet, using her left hand to wipe at her face.  People were staring, and she couldn't bring herself to care.



She looked back, and she could see her dad there, back to a divider between store displays, one toe raised, as if the scuff marks in the hard brown leather were of great interest.



``I think,'' Taylor said, very carefully, ``I'm going to go.''



``I wish I could say more, but we could talk again.  You could explain, if you were up to it.''



Taylor shook her head.  ``I think this is something I have to figure out myself.''



``Go with your gut, then.''



``But thank you.  Before we talked, I wasn't sure it was something I could figure out, and now I think it might be doable.  I feel like it's\ldots clarified.''



``Good.''



``And I \emph{would} like to meet and talk again.  About something less heavy.  Maybe about books?''



Annette smiled.  ``It's a date.''



Taylor smiled back, then wiped at the tears again.  She grabbed her bag, slinging it over her good shoulder, then made her way to her dad.



She stopped in her tracks.



In the crowd, a boy with dark curls, a little bit of a slouch, and a white t-shirt.



\emph{Alec}?



\sectionbreak



Tattletale watched on her monitors as the others migrated downstairs.



Only Imp and Rachel remained.



``Okay, so he's\ldots what?  This is dumb.''



``You were supposed to be explaining,'' Rachel said.



``I \emph{was}, but this is so dumb I can't wrap my head around it.''



``\emph{What's} dumb?'' Rachel asked.  ``If you don't answer, I'm feeding you to Bastard.  I don't want to do that.''



``Aw, you care!''



``Wouldn't be good for him,'' Rachel said.



Imp sighed.  ``Teacher's plan.  It's dumb.  We're supposed to worry about this shit?''



``No,'' Tattletale said, watching on the monitors as the others from the meeting made their way downstairs.  ``Teacher isn't a threat.  Or he isn't a big one.  You were talking symbols before?''



``Symbolic shit, yeah.''



``Consider Teacher a symbol.  Things are starting into motion, the quiet is coming to an end, and he's\ldots if not a threat, he's a gatekeeper to one.''



``He's a smug dick,'' Rachel said.  ``You give the go-ahead, we tear him apart.''



``It's a little more complicated than that,'' Tattletale said.  ``There are dynamics to pay attention to, group interactions, politics, there are unwritten rules, and the nuances of what happens if and when \emph{we're} viewed as the aggressors when we violate the truce.  Not to mention the danger if we disrupt whatever he's setting up and inadvertently set it off.  Like we sort of did with Jack, though that was more exception than rule.''



``Orrrrr you could give the go ahead, we cut past all the bullshit and we tear him apart,'' Rachel said.



Tattletale sighed.



``Lemme hash it out for you,'' Imp said.  ``You know how Tats said he's like the gatekeeper?  He's like an asshole, standing in the middle of the elevator doors so they won't shut.  You can kick him in the balls, but then you've got to deal with his \emph{friends,} you're dealing with being the jerkass that kicked someone in the balls and you're maybe dealing with the big bad motherfucking dude that just came up in the elevator, who wasn't coming out because there was someone in the way.  Someone you \emph{removed} from the way by kicking him in the balls.''



``Oh damn it,'' Tattletale sighed.



``Okay\ldots'' Rachel said.



``You did \emph{not} just get her metaphor,'' Tattletale said.  ``Don't do this to me.''



``Can we kick him down the elevator shaft before the big guy comes up?''  Rachel asked.



``Fuck it,'' Tattletale swore.  ``And fuck you, Aisha.  Yes.  Theoretically, we could put the kibosh on him before he gets far enough in his plans.''



``Good,'' Rachel said.  ``Then it's settled.''



Imp pulled off her mask, just to show Tattletale how much she was grinning.



``Keep that up and I'm telling those Heartbroken kids you ate cupcakes while they waited downstairs,'' Tattletale said.



``No,'' Imp said.  ``Nope.  Nuh-uh.  You would be signing my doom warrant.''



``Doom warrant?  Nevermind.  I think we have an understanding,'' Tattletale said, grinning as much as Imp had been a moment ago.



``That's it, then?  A big bad that needs dealing with, a few little bads that need an organized clean up job, and we stay in touch,'' Imp said.



``That's the gist of it,'' Tattletale said.



``Cool.  Great.''  Imp said.  ``Excellent.''



Her eyes slowly traveled to the red wine-stains in the carpet.



``Yeah,'' Tattletale said.  ``So.  Now that the others are gone and there's no need to pretend anything, it's your chance to say.  You guys good?  Copacetic?  We good to go?''



``Sure,'' Rachel said.  ``I'm not sure I really get what all \emph{this} was, but I kind of liked it.  Made me feel better, where I didn't realize like I felt \emph{bad}.  Less lonely, maybe.''



``Yeah, no, I get that,'' Imp said.  She shrugged, putting her mask back on as Tattletale opened the door.  They filed out.  ``Yeah.  Except I guess I can say it wasn't loneliness for me, while we're being open and shit.''



Tattletale nodded.



``It was good,'' Imp said.  ``Weird, but fitting.  I'm wondering why you invited the twit, though?''



``Which twit?''



``Our kid Cassandra,'' Imp said.



Tattletale blinked once or twice.  ``Where the fuck are you getting these references from?''



Imp only allowed herself the smallest giggle, exceedingly pleased with herself.



``I think\ldots it was maybe one of the big reasons I wanted to do this,'' Tattletale said.  ``It was important that I showed her that Taylor was dead.  I had to convince her.''



``Convince her?''  Imp asked.



Tattletale nodded.



``You'd think she'd be really good at figuring that basic shit out on her own.''



``You'd think,'' Tattletale said.  ``But no.  We're really good at lying to ourselves.  Take it from another thinker.''



``Fuck,'' Imp said.



``Fuck,'' Tattletale agreed.



``So,'' Rachel said.  ``What happens?''



``What happens is we go kick teacher in the balls and drop him down an elevator shaft,'' Tattletale said.  ``Hopefully in a way that doesn't leave us looking like assholes.''



Rachel nodded, satisfied.



``And Taylor?''  Imp asked.



``I'll keep looking after things in that department,'' Tattletale said.  ``If that's cool?''



``That's cool,'' Imp said.



They made their way down the last two flights of stairs.



The assembled forces of the Undersiders waited, the other guests having already departed.



Twenty soldiers, only a small share of Tattletale's full organization.  The kids, the Heartbroken, and Aiden, all together, playing with Forrest and Charlotte standing warily by.  Parian and Foil, sitting in a windowsill, with snow piling behind them, and Rachel's escort with each member of the gang having a dog with them.



``All good?'' Tattletale asked.



``Fuck yeah,'' Imp said.



``Mm,'' Rachel offered a nonsyllabic response.



\sectionbreak



Taylor shook her head a little.  The resemblance was slight, if it was even there.  Her mind was playing tricks on her.



Her hand touched her forehead, and she felt a pair of soft spots, each barely wider across than a dime.  She ran her hand over her short hair.  She didn't know how it had happened, but she could guess.  Bullets to disable her, surgery to seal her power away.



Cauldron, apparently, did have a means of locking powers away.  Or maybe it was Contessa, doing the work, or perhaps she'd simply been kept alive, carted to Panacea or Bonesaw, who could fix things up.



But dwelling on those things wasn't healthy, and it was pointless in the end.  She'd likely never get a serious answer.  She only had the two dimples or holes in her skull, the sole apparent casualty of some kind of brain surgery.



\emph{Apparently}.  Such was the momentary crisis she'd experienced, seeing someone who was supposed to be dead.  She had been left to \emph{wonder}, for heart stopping seconds.



``You done?'' her dad asked.



``Done,'' Taylor responded.  ``It wasn't her.  I knew it going in, but it wasn't her.''



``Yeah,'' he said, quieter.  He put one arm around her shoulder.  ``You okay?''



``That's a hell of a question to answer,'' she responded.



``Yeah.''



``I feel better.  It was a hell of a good hug.''



He smiled, but there was sadness in his expression, ``A little bit like her then.''



Taylor nodded.



``Lunch?'' he offered.



``Lunch sounds good,'' she said, resting her head against his shoulder as they walked.  Her injury, the brief delirium that had followed her awakening, the lack of an arm and her struggles to learn to use the artificial one, it had gone a long way.  He'd needed a chance to be a parent again, and she'd needed a parent.



They were okay.  They were safe.  If and when a problem came up, if it somehow reached this sealed off Earth, she could stand by to let someone else handle it.



She'd done her share.



There were things that would be harder.  Even now, she couldn't think too hard or in certain directions, or guilt and memories of another \emph{her }that she'd seen all too clearly would emerge.  More recent, scarier in a way, was the lingering doubt, a belief that things \emph{couldn't} work out, ingrained in her by experience.  The idea that any reality where life \emph{did} work out on any level wasn't reality at all, or that it wasn't \emph{life}.



She spoke her thoughts aloud.  ``I think\ldots there's a lot of stuff bothering me.''



``Only natural,'' her dad said, very carefully.



``But I've dealt with worse.  If it comes down to it, if this is all I have to worry about, I can maybe deal.  I could maybe learn to be okay.''



``I think that's all any of us can hope for,'' her father said.





