





I stared down at the metal walkway as I caught my breath.  I had one gash at the side of my head, and another trickle ran from beneath the armor of my shoulder, down my arm and to my fingertip, where it dripped almost in sync with the head wound.  It should have hurt, but it didn't.  Maybe it would when the shock wore off.  If so, I didn't look forward to it.



Trickster, Ballistic and Circus lay in front of me.  Another cape had fallen over the railing and lay on the concrete floor below, unmoving.  They were all either unconscious or hurting badly enough that I didn't need to worry about them.



I swallowed hard.  My heart had climbed up so far into my throat that I almost couldn't breathe, and my heartbeat felt oddly distant and faint for how terrified I was.



Coil's base was deserted.  I knew his men were out on patrols, that the only people in here were a handful of the capes that were working for him.  He'd left it almost undefended.



If I was going to act, I'd have to do it now.



My costume's feet lacked hard soles, so I should have been nearly silent, but the interior of Coil's base was deathly silent and my feet were slamming down on the metal walkway as I ran.  The noise of singing metal filled the dark space, echoing, seemingly louder with each step I took.



The thrum of the metal rang through the air even after I came to a stop.  I'd reached my target; a reinforced door, identical to so many others in the complex.  With the labyrinthine mess of metal walkways and the dozens of doors, I might have missed it.  The only thing telling me I was in the right place was the smudge of ash left behind from when the soldier had put out his cigarette on the wall.



I opened the door, and it was far too loud, creaking, then banging into the wall with a crash despite my last-second attempts to stop its momentum.



The room looked like a prison cell.  It had concrete walls and floor, a cot and a metal sink and toilet.  Coil and Dinah were both there.  I couldn't say whose presence left me more devastated.



I could say Coil's presence was the worst thing, because it meant my info was bad.  His power meant I was probably fucked on a lot of levels, that the odds were suddenly astronomically against me.  I was caught.  My gut told me that I wouldn't make it out of the compound in one piece, now.  He was washing his hands in the sink, he turned to look at me, apparently unconcerned by my presence.



But no.  As I stared at Dinah and registered what I was seeing, I realized the image would be burned into my mind's eye forever.  She lay on the cot on her side, her eyes open, staring at me, through me.  A bloody froth was drying at one side of her mouth and at the edges of one nostril.  I didn't consider myself a religious person, but I prayed for her to blink, to breathe, to give me some relief from that cold horror that was gripping me.



I was too late.



My vision practically turned red as I charged Coil, drawing my knife as I ran.  I felt him use his power, and suddenly there were two of him, two of me, two cells with two dead girls named Dinah Alcott.



In one of those rooms, I stabbed Coil in the chest.  There was no satisfaction in doing it, no relief.  I'd lost, I'd failed in every way that counted.  The fact that I'd put him down barely mattered.



In the other room, he stepped back out of reach of my first lunge, raised one hand and blew a handful of pale dust into my face.  While I was blindly slashing in his direction, he grabbed the wrist of my knife hand and held it firm in his bony hand.



That room where I'd succeeded in stabbing him faded away.  The only me that existed, now, was coughing violently.  My knees buckled as I coughed hard enough to bring up my lungs, unable to get the powder out of my nose and mouth.  I pulled at my hand, trying to free it from his grip.  Futile.



``Stop,'' he ordered me, and my struggles stilled, though I was still finishing my coughing fit.



``Diluted scopolamine,'' he spoke, his voice calm, sonorous.  He let go of my wrist, and pushed at the knife in my hand.  I let it drop.  ``Also known as Devil's Breath.  The vodou sorcerers, the Bokor, were said to use this along with the venoms of the puffer fish and other poisons.  With these substances, they could create the `zombies' they were so famous for.  These zombies of theirs were not raised from the dead, but were men and women who were forced to till fields and perform crude labor for the Bokor.  The uneducated thought it magic, but it was simple chemistry.''



I waited patiently for him to continue.  The notion of fighting or responding didn't even occur to me.



``It strips imbibers of volition and renders them eminently suggestible.  As you can see, I attempted to use it on my pet, and the results were\ldots tragic.  The price of hubris, I suppose.''



He sighed.



``Take off your mask,'' he instructed me.



I did.  My hair fell across my face as I let my mask fall to the ground.  My cheeks were wet with tears.  Was that from before, from when I'd first seen Dinah?  Or was I able to cry about my present circumstance, even if I was helpless to do anything about it?



He touched my cheek, brushed a tear away with his thumb.  He stroked my hair, and the gesture felt strangely familiar.  The way his hand settled on the back of my neck and gripped me there didn't.  It felt\ldots possessive.



``Pet,'' he intoned, and fresh terror shook me to my core.



``You couldn't have succeeded.  This was terribly unwise.''



``Okay,'' I murmured.



\emph{No, no, no, NO.}



I didn't deserve this.



My eyes fell on Dinah.  She still stared at me, eyes wide and unblinking, and I couldn't help but see the look as accusing.



I \emph{did} deserve this.  It was thanks to me that she'd been kidnapped.  Thanks to me that she'd been made into Coil's slave.  Karma, perhaps, that I'd take her place.



The strength went out of me.  My head hung, and I stared at my feet.



Tears streamed down my face.  I didn't wipe them away.  I wasn't sure I could.



``Look at me, pet,'' Coil instructed, and I did.  I was glad to, like a compliant, eager to please child.  A part of me wanted more orders.  In that drug induced haze, I wanted to lose myself in obeying, wanted to serve.  That way, at the very least, I wasn't to blame for my own actions or the tragic consequences that followed from them.



Coil removed his mask, and I stared.



I recognized him.  He was someone I knew all too well.



They were both tall, thin.  How hadn't I seen it?  Coil's costume could must have been designed to highlight his skeletal structure, make him look thinner and more bony.  All it had taken, beyond that, would be an affected change to his voice and different mannerisms.  I'd been unable to see it.



So dumb, so stupid.



I could understand it, too.  He'd been struggling to fix things, watching people failing to find work, knowing it was the city government that was to blame.  I could remember him telling me how he'd make the city work again, how he had all the answers.  I knew how hungry he was to do it.



He'd gotten powers.  He'd started to put plans into motion so he could do just that.



``Welcome home, pet,'' he spoke, and he didn't speak in Coil's voice.  The voice I heard was my father's.



\sectionbreak



I woke up, and for a long moment I stared up at the ceiling of my room and reassured myself that it was all a fabrication of my own scumbag mind.  It had been a nightmare or a terror dream; I wasn't positive on the differences between the two.  It was my brain drawing together all my guilt about what we'd done to Shadow Stalker, the role I'd played in Dinah being kidnapped and leaving my dad; knitting it all into some convincing, disturbing scenario.  Not the worst I'd had, but there was at least some repetition and familiarity with the usual ones.



\emph{Fuck.}



It had felt way too real, and it had \emph{sucked}.  My shirt stuck to me with the damp of my sweat, the room was warm, but I still shivered.



My alarm clock sat on the ground by my inflatable mattress.  I picked it up and turned it around so the I could see the green numbers of the digital display.  Five forty in the morning.



Time to wake up, I supposed.  There was no way I was going to be able to fall asleep again in the next few hours.  It wasn't just the idea of having another nightmare.  The dream had left me with a feeling of an impending deadline.



How long could Dinah be expected to hold on?  I doubted Coil was taking bad care of her, so she wouldn't die of malnutrition or overdose on whatever drugs Coil was giving her.  Still, there was a limit to what the human mind could handle.  How long until Coil pushed her abilities too far?  If she was getting headaches from the use of her power, there was a chance she could suffer more severe issues if pushed to use it more often.  Pain \emph{generally} signified something was wrong.



I was also worried I wouldn't earn Coil's trust and respect.  Until this was resolved, I wouldn't be able to rest, take it easy, or have a day to myself.  Not in good conscience.  Depending on what happened, it might be a long, long time before I could relax again.



What worried me more than anything was the idea that I might save Dinah, only to find that Coil had broken her spirit or her will to the point that she couldn't go back to her old life.  I worried that, like in my nightmare, I would be too late.



With this in mind, I sat up and tossed the sheet aside.  I reached for my glasses, by the alarm clock, then stopped.



Instead of putting on my glasses, I stood and made my way to the bathroom adjacent to my room.  Alongside fresh supplies of toothbrush, toothpaste, soap, tweezers, shampoo, conditioner and all that, I had a small box with packages of disposable contact lenses, daily use.



I hated contacts so, so much.  I'd tried them in middle school, at Emma's recommendation, and they had \emph{never} felt comfortable.  That, and I had never figured out how to put them in properly.  It seemed like ninety-nine out of a hundred times, they flipped inside out to cling to my fingertip instead of sticking to my eye.



True to form, it took me four minutes to get the contacts in, and I found myself blinking every two seconds after I \emph{did} have them in.



At least I could see.



I walked through my new base of operations wearing an oversized t-shirt and a pair of underwear.  Not exactly fitting attire for a supervillain.



My new abode was three stories tall, which made it taller than Grue or Bitch's places, which were the only ones I'd seen thus far, but it was narrow.  A cafe had stood here, before, but it had been flattened by one of the first waves to hit the city.  Coil owned at least one of the companies that was managing the restoration and reconstruction efforts, and over the past two and a half weeks, as his crews had started clearing and rebuilding on the Boardwalk, he'd had them set up some buildings, all squashed together.  When the Boardwalk was fixed up, these same buildings would be at the westmost edge of the same block that had the stores, restaurants and coffee shops.  If the Boardwalk ever got going again, they would be prime real estate.



Ostensibly to protect these new buildings until people started buying up the properties, each had been set up with heavy metal shutters to seal the windows and wall off the front.  It made the building dark, with only faint streams of light filtering in through the slats at the top of each shutter.



The topmost floor was mine and mine alone.  Taylor's.  It was living space, with a bedroom, bathroom and kitchen.  The bedroom was spacious enough to serve as a living room as well as a sleeping area.  The first things I'd done after Coil's men had unloaded the furniture and supplies was to hook up an internet connection and computer and get my television mounted on a wall and connected to a satellite.



The second floor, as I liked to think of it, was Skitter's.  It was for my costumed self.  It still needed more than a few things to complete it.  I flipped a switch in the stairwell, and tinted flourescent lights lit up on the undersides of the shelves that ran along two adjacent walls, floor to ceiling.  Each shelf was lined with terrariums and backed by strategically positioned mirrors so that the light filtered through the front of the terrariums and into the room.  Only a few were occupied, but they each had the same general contents – a layer of dirt and pieces of irregularly shaped wood.



I hit the second switch, and chambers in the lid of each occupied case opened to release their inhabitants.  As they crawled through the case, the spiders were lit up by the lighting so that their shadows and the strange shapes of the wood were cast against the panes of hard plastic, distorted and larger than life.  I'd seen a picture on the web of the same thing, done on a far smaller scale.  I had hopes that the effect would be suitably impressive and intimidating once all of the terrariums were full.



It would be doubly impressive once Coil's special effects technician stopped by and outfitted a case with a series of switches that a large bug could move – a beetle or something.  If I could direct the beetle to release the bugs, turn the lights on or off or even open the lids of the terrariums, all while appearing to sit motionless in my chair, it would be that much more effective for any audience I happened to have in the room.



Terrariums aside, the room was sparse.  Six empty pedestals sat just beneath the shuttered window, each standing just a little beneath knee height.



After touring the place yesterday morning and spending some time browsing the web to see what was available, I'd gotten in contact with Coil and named every possible thing I could think of that I could use for the space.  The current contents of the rooms on this floor and upstairs had been delivered last night.  The stuff I was waiting on was harder to come by, and it would be unreasonable to expect it to be available and in place within this short span of time.



I did have a chair, here, way too large for me.  It was positioned in one corner, so that it was framed by the two walls of terrariums.  It was black leather, and broad enough that I could comfortably sit cross-legged on it.  I'd loved the idea since I'd seen one like it in Brian's apartment.  It was the one concession I was making in regards to atmosphere and appearances.  A series of smaller seats were positioned so they faced the larger chair and the terrariums.



A large abstract painting hung above the stairs on the right side of the room.  I'd seen a similar one online and had liked it, so I had found the artist's gallery and stumbled onto this.  It was the first thing I had asked Coil for, and he'd delivered a large framed print far faster than I might have expected.  I liked how it tied into the room and echoed the shapes cast against the front panes of the terrariums.  The black lines were painted on the background of reds and yellows in a way that seemed \emph{spidery}.



I stared at the painting for a minute, seriously worried that I would see the abstract image from a different angle and realize I'd had Coil get me a eight-foot by five-foot painting of a hairy wang or a headless chicken or something.



Making my way down the stairs, I found the ground floor surprisingly cool.  The weather was warming up, and with the shutters closed, I'd found my room warm, sticky in the humid air.  I'd foregone pajama bottoms, had slept with just a single sheet, and had slept with my feet uncovered.  Goosebumps prickled my bare legs as I stepped on the cool hardwood floor.



The ground floor here wasn't much different from the one at Grue's place.  There was an area with bunk beds, albeit fewer than Grue'd had, a bathroom, a small kitchen and an open area that didn't yet serve a purpose, stacked with boxes.



All this was mine.  My lair.  It felt so empty.



I knew that would change as it filled with furniture and necessities.  The place was already something of a luxury.  More than half of Brockton Bay was currently lacking plumbing or electricity, with more than a few unfortunate individuals having neither.  In the process of setting up these buildings, Coil had ensured I was provided with both.  Trucks would be coming and going through this area as clearing and construction continued, and Coil had informed me that these trucks would be discreetly resupplying me with water, ensuring my water heater had propane, emptying the aboveground septic tank and refueling the generator.



As the city was rebuilt and standard utilities were put back in order, these special measures would be set aside, I'd get hooked up to \emph{those}, and my lair would be lost in the surge of urban growth.  Ideal world.



It was nice to be able to enjoy those luxuries, but the Dinah situation took all of the joy out of it.  I had hot showers and the ability to wash my dishes because \emph{Coil} had provided them.



I grabbed a cell phone from the kitchen counter and dialed Coil.  I didn't give a fuck about the fact that it was 5:45 in the morning.



It bothered me, calling him, relying on him.  It made me feel complicit.  Inconveniencing him, even a little, felt good.



``Yes?''  His question was curt.



``It's Skitter.''



``What is it, Skitter?''



``I need a loan of some guys.''



``How many?''



I looked around the living room, ``Eight?  A truck would be a good idea, if you can get one here.''



``I can.  These men you require, are you needing gunmen or-''



``Just regular guys, anyone up for some exercise.''



``I assume there's no rush?''  He was being more curt than usual.  Maybe I'd woken him up.  I didn't really care.  He could deal, if I was working on something that helped him.



``No rush.''



``Then I'll have them there in an hour.''



``An hour, then.''



He hung up.



It was a lot of time to kill.  Free time sucked when you didn't want to be alone with your thoughts.



I wanted to run, but it was awkward.  The fenced off areas, construction zones and flooded streets of the Boardwalk didn't really make a sprint around the neighborhood that doable.  Besides, it was dangerous enough I might stand out.



In the end, I went against my better judgement and decided to go for a run.  I dressed in a pair of shorts and a tank top, donned my running shoes and ensured I had both my pepper spray and my knife.  I unstrapped the knife's sheath from the back of my costume, then threaded a belt through it so I could strap it around my waist.  I put the sheath itself under my waistband and the handle of the knife under my top.



I stood in front of the full length mirror in my bedroom to check how visible the weapon was.



It wasn't exactly hidden, but it wasn't conspicuous either.  I adjusted it slightly, then called a small collection of bugs to me.  It was a little creepy, having them crawl on my skin, beneath my clothes into my hair, but that stopped when they reached their destinations – above my socks, in my hair and between my bra and my top.  I was cool with it so long as they weren't directly on my skin.



Did I look different?  My skin had a light tan, now. I'd spent more time outdoors in the past few weeks.  In the week and a half I'd spent in the shelter, I hadn't exactly had books or TV, so I'd walked during the day, making my way across the city to check on the loft and to see the state of my dad's house.  I'd walked at night, too, when I'd been unable to sleep, but people hardly tanned doing that.



I couldn't pin down exactly how or why, but the definition in my face and body had changed.  It was possible I'd had a growth spurt.  Some of it was perhaps the tan giving more accent to the features of my body or face.  Maybe it was that I'd been eating a pretty lean diet when I was staying at the shelter, coupled with the fact that I'd been so active over the past two months.  I hadn't spent six hours every day sitting around in school, I'd been in fights, I'd been running, and I'd ridden the dogs.  I had some muscle definition in my arms, now, and I thought maybe I was standing straighter.  Or maybe it was all those minor things helped by the simple fact that I was dressing differently, that my hair hadn't been cut in a while, and that I wasn't wearing my glasses.



To say I barely recognized myself was.. how could I put it?  It was \emph{true}, but I could also remember myself months ago, when I'd look at my reflection and I would be so focused on the flaws and the things I didn't like about myself that I never felt familiar with the person I was seeing in the mirror.  It was as though it was always a stranger I was looking at, and I would be left vaguely surprised at the combination of features across from me.



This was not recognizing myself in a very different way.  There were still things I didn't like, like my wide mouth, my small chest and the lack of curves or any real femininity.  My scars stood out with my slight tan, a teardrop shaped mark on my forearm where Bitch's dog had bitten me, a wavy mark on my cheek where Sophia had dug her fingernails in,and a line by my earlobe where she'd tried to tear my ear off.  But my physical flaws no longer consumed my attention when I looked at myself. I felt comfortable with my body, like I'd somehow earned it, the way it was, and it was \emph{mine} now.  I wasn't sure if that made any sense, even to myself.



If there was anything about myself that I didn't like, it was primarily psychological.  Guilt was a big one.  The idea that my dad might dislike me if he got to know me, now?  That was another.  That my mom, were she alive and showing up at the door, might be disappointed in me?  Sobering.



As he'd done with his own underground base, Coil had set my lair up with a discreet entrance and exit.  Leaving through the front door would be conspicuous, if I started working with anyone beyond my teammates.  Skinny teenage girl with black curly hair entering and leaving the same building that the skinny teenage villain with black curly hair was operating out of?  No.



I made my way to the building's cellar, opened a hatch and entered the adjacent storm drain.  The same builders that had put the building together had blocked off the drain so the water flow wouldn't make it impassable, and I was left with a clear route down to the section of beach where the storm drains emptied.



I wasn't sure if Coil had plans to keep the city's workers from trying to unblock the drain, but I supposed that was the sort of thing we could rely on him to handle.  In the meantime, a third of the storm drains were too clogged with rubble and detritus to drain, and another third didn't connect to anything anymore.  Add the fact that most of the storm drains were a little out of the way of regular foot traffic, and it wasn't too conspicuous.



I started running the moment I reached the beach, glad for the chance to resume my routine.



It was a strange environment, eerie.  The wooden pathway, the literal boardwalk that had run in front of the stores, was now a skeletal ruin that loomed above the piles of trash that the bulldozers had all pushed to one side, twice as tall as I was.  The beach had been cleared, which was a feat unto itself.   The work of the bulldozers and the crews with rakes had revealed the packed, dirt-like layer from beneath the loose sand.  Opposite the trash piles, by the water, there were mounds of irregularly shaped pieces of concrete, set to break up the waves and prevent the highest tides from dragging the trash, debris and machinery into the ocean.  Two mounds looming on either side, with a space cleared in the middle for the trucks and any foot traffic.



A scene up ahead caught my attention.  Two pieces of machinery lay in a heap just below the lip of the boardwalk above.  A bulldozer and an eighteen wheeler with a crane-mounted claw attached had both been driven or pushed over the edge of the boardwalk and onto the beach.  The cab of the truck with the claw had been partially crushed by the bulldozer. Though it was barely past six in the morning, a group of laborers were already there, some on the ledge above, others down on the beach, all gathered around the trucks.



Spray paint had been used to draw the same crude symbol on both the side of the eighteen wheeler and the concrete wall separating the beach from the Boardwalk above.  A capital `M', with two taller lines drawn vertically through it much the same as you'd do with a dollar sign.  The Merchants.



It fit their modus operandi.  They had been bums, drunks and addicts, looked down on others, before Leviathan came.  In the wake of what Leviathan had done to the city, leaving everything in shambles, with social services gone or in chaos and even basic utilities in short supply, everyone else had been brought down to their level.  The Merchants were even, I suspected, thriving.  With strength in numbers and virtually nothing holding them back, they had become like pack animals.  They roamed the city in bands of three to twenty, robbing, raping, pillaging and stealing.  They were settling in some of the better areas, the neighborhoods that still had power or water, and forcing the existing residents out.



Or, worse, I could imagine that some were moving in and keeping the residents around for their own amusement.  It was not a pleasant thought.  The kind of people who had gravitated towards the Merchants tended to have a lot of resentment.  Specifically, they had resentment towards people who had what they didn't.  If they happened upon a family with Kate the soccer mom, Tommy, the kid with more video games than teeth, and Joe the blue-collar worker with a steady job?  If they weren't letting them go?  I was guessing that hypothetical family would be in for a hell of a rough time.



It might have sounded silly, that line of speculation, but I'd spent time in the shelters.  I'd heard about how vicious and depraved the Merchants were getting.



Anyways, this?  This whole situation?  They liked it.  They wanted to keep things this way, and that meant they were going to stop anyone else from fixing it.  They would intercept supplies, attack rescue workers and they would push construction vehicles into a heap on the beach.



I'd have to deal with these guys.  It wasn't just intercepting any groups that made their way into my territory.  That was easy, all things considered.  No, I also had to deal with the small army that would come marching through here wanting retaliation over my having kicked the asses of any groups that had made their way into my territory.



I could call on the others, if such a situation arose, and I expected them to call on me if the same thing happened.  But people would take time to get here, and the Merchants, the Chosen or whoever else was making trouble could \emph{keep} making trouble until the reinforcements arrived.  It was tricky, and I didn't know for sure how I'd handle things if-



``Taylor.''



My reaction wasn't much different than if someone had stabbed me in the stomach with an icicle.  I'd thought of that mental image in particular because of the cold, horrible feeling in my midsection; fear, guilt.  My thoughts immediately went back to my nightmare from earlier.  I turned to look.



``It's you,'' my dad spoke, ``Wow.''



He stood on the ledge above me.  He was more tanned than I was.  He wore a short-sleeved button-up shirt and khakis and held a clipboard.  It set him apart from the other laborers, and the man who stood just behind him, wearing a gray t-shirt and jeans.  I knew in an instant, my dad was in charge around here.



Looking at him, I couldn't imagine how I might have thought he was Coil.  Even in a dream.



``Just out for my regular run.''



Surprise etched his face, ``You're running during this\ldots?!''



He made a visible effort to close his mouth.  It made me feel uneasy.  What thought process or concern was keeping my dad from opening his mouth about my running?  He'd been worried about it when the streets were relatively safe.  Was he \emph{that} spooked at the idea of scaring me off again?



He looked at the man who was standing near him, murmured something.  The man walked over to join the others in observing the damage around the damaged vehicles.



We were left more or less alone.



``You got my messages?''  I asked.



``I've listened to that answering machine so many times-'' he stopped.  He was a good distance away, but I could see the lines in his forehead, ``I miss you.''



``I miss you too.''



``I\ldots I don't know how to ask.  I'm afraid to ask you to come home, because I'm not sure I can stand to hear you tell me you won't.''



He paused, for a long moment.  Waiting for me to jump at the opportunity.  I stayed silent and hated myself for it.



``Well,'' he said, so quiet I could barely hear him, ``You can always come home.  Any time, any reason.''



``Okay,'' I told him.



``What are you doing with yourself these days?''



I struggled to find an answer, and was saved by the bell.  One of the men by the wreck shouted, ``Danny!'' and my dad turned.



My dad ran his fingers through his hair, ``I need to go handle this.  Can I\ldots How do I contact you?''



``I'll leave you a message on your answering machine,'' I said, ``With my cell phone number, and my email in case I'm in an area where cell service is down.''



``Email?'' he asked.  ``Where are you that you have access to a computer?''



\emph{A few blocks from here}.



``Just outside the city limits,'' I lied, ``Not far from the Market.''



``So you're out of the way of any trouble,'' My dad noted, with a touch of relief.  There was a noise as someone began prying one of the truck doors open, and my dad turned his head, frowning.  ``But what are you doing here this morning?''



``I was going to stop by the house, see if it was in okay shape,'' I lied again.  Was this the extent of my interactions with my dad?  Always lies?  ``Keeping up with my running.''



``I see.  Look, I have to go, but I do want to talk again, soon.  Lunch, maybe?''



``Maybe,'' I offered.  He offered me a sad smile, then turned to go.



I moved my hand to adjust my glasses, and wound up waving at my face.  I was wearing my lenses.



``Dad!'' I called out.  He stopped.  ``Um.  I'd heard the Slaughterhouse Nine were around.  Be careful, warn others.''  I pointed at my face.



His eyes widened.  I could see the thought process, the realization.  He took off his glasses and hung them from his shirt's front pocket.  I wasn't positive that was much better.



``Thank you,'' he said, squinting slightly at me.  He raised a hand in an awkward half-wave, and I returned it with one of my own.  As if by mutual agreement, we turned to leave at the same time, both of us going in separate directions.  He hurried to where he was needed, and I turned to run back to my place.  My lair.  I hadn't run nearly as far as I'd wanted, but I wasn't up to continuing.



I checked the kitchen clock as I entered from the cellar.  I had thirty minutes.  I took the time to shower and don my costume – my sleeve was still crusty and stained yellow-white where it had come in contact with the foam, but at least it wasn't sticky anymore.



My mask wasn't wearable with the contacts.  I'd taken lenses out of an old pair of glasses and set them into the construction of my mask.   I debated it for a few moments, then I decided to use the remaining time to fix it.  With my knife's point, I set about undoing that particular piece of work, prying the lenses out.



I finished with enough time left over to grab and eat a breakfast bar.  Coil's people were punctual, rapping on the metal shutter at six forty-five.



Alright.  This was it.  I pulled on my mask.



Time to claim my territory.





