





Water sprayed in the truck's wake as we cut a path through the flooded streets.



It was a military vehicle.  I wasn't one to know much about cars, and I knew even less about stuff like military vehicles, so I couldn't put a name to the truck that was carting me and eight of Coil's workers through the Docks.  It was like a sturdy pickup truck, but the rear section was wider and it was hidden beneath a green tarp that had been stretched over a framework of metal bars.  The tires were massive, with deep treads allowing the truck to navigate all but the most cracked sections of road where Leviathan had brought the underground pipes and drains through the surface.



The interior was loaded with the supply crates that I'd had Coil's guys load into the vehicle.  Each set was strapped together and tied down to the floor and sides of the truck with belts.  There wasn't much room for the seven of us in the back, and we'd been forced to sit on the crates with little legroom.



A part of me wanted to converse with Coil's men and get to know them.  Another part of me, a larger part, told me that I shouldn't.  I had to convey power and confidence.  I wasn't sure I could do that while making small talk.  With much the same reasoning, I'd chosen not to help with the loading of the truck.



The men Coil had sent me were dressed up in the same outfits worn by the cleanup crews I'd seen around the city, picking up debris, trash and dead things.  They wore heavy plastic one-piece bodysuits, made of a material I compared to those heavy-duty industrial rubber gloves that my dad kept under the sink, each in blue and yellow.  The suits were loose-fitting, and only the upper halves of their faces were visible behind the clear plastic goggles they wore.  Their mouths were hidden by the filters intended to prevent mold, dust and airborne pathogens from getting into the worker's lungs.



The masks also, I noted, did a good job at hiding the identities of the six men and two women.  If it weren't for that, I'd think Coil was trying to be funny, giving the hazmat crew to the bug girl.



Whatever image I conveyed, whether it was in the role of a leader or as a potentially dangerous villain, it had given me elbow room.  Coil's employees had chosen to sit, cramped together, closer to the rear of the truck.  I sat atop a crate with my back to the truck's cab, watching the road behind us.



In a way, it was good that I wasn't engaging in conversation.  It let me focus on what I needed to – my bugs.



Generally speaking, there were two routes I tended to go.  The first put me in one spot, drawing my bugs from the area.  A three block radius made for a good number of bugs.  The second situation came about when I'd taken the time to gather a few select bugs from here or there, while covering a whole lot more area.  I'd done it before the bank robbery, to get a prime selection of bugs.  I'd also done it before we attacked the ABB the first time, with the other groups.  Never enough to draw attention.



This was different.  This time, I wanted attention.  This time, the city was a breeding ground for the bugs.  Warm, moist, and filled with food.  This time, I was gathering everything I could \emph{and} I was covering a lot of ground.



We'd been driving for fifteen minutes around the perimeter of what I hoped would be my territory, gradually closing in towards the center.  I found the bugs closest to the edges and sent them toward the middle.  Of the ones that could fly, I had them gather overhead.  It was more bugs than I'd ever controlled at once.  My power seemed to crackle in my head as I drew in and interpreted all of the data.



I was almost convinced I would finally see the upper limit of my power.  That I'd reach for more bugs and realize I couldn't control any more.  It didn't happen.



The clouds of bugs that were gathering in the center of my territory were starting to cast a visible shadow on the area.



They weren't the only bugs I controlled.  I had others on separate tasks.  With a number, I created barriers, heavy clouds in alleyways and across streets.  My motives here were purely selfish – I laid these barriers between the southmost end of the old Boardwalk and the Docks because I didn't want my dad entering the area.  My gut told me that if he got a good look at me in costume, he'd know who I was.



Besides, it didn't factor into my plan.



I had other bugs sweep through the inside of the buildings in my range.  I made contact with people, stirring some from their sleep.  As I sat on the crate in the back of the truck, nearly motionless, I was making a tally.  How many people were here, and where were they?



When I had a sense of things, I began organizing my bugs into formations.  I started in the areas with lots of people clustered together: a warehouse with no less than eighteen people; a tenement crammed with what I assumed were families, with lots of small children; and an overly warm building with a large group of half-dressed people drenched in sweat.



As I got those groups out of the way, I turned to targeting smaller groups, probably collections of families or friends.  Where people were too deep in their sleep, I had the bugs nip at them to wake them.



They would wake up and see what I'd done.  On their walls and floors, much as I'd done at the fundraiser, I had my bugs organized into arrows, pointing the way out the doors, down to the streets, and towards the truck's destination.  I drew out the letters to the word `supplies' and left them in the brightest lit, warmest spots in the rooms where people were.  Accounting for the illiterate, I put the bugs down in the shapes of basic food – a drumstick, a cut of cheese, a can.



I knew I wasn't the best artist.  I worried I was confusing matters with the pictures.  I could only cross my fingers.



Today wasn't one of the days my power was working double time, with double the range.  I'd wanted to make sure to reach as many as I could, so I'd started drawing the arrows and words with the bugs early.  The unfortunate downside of that was that it meant we were left with barely any time to set up after we arrived at our destination.  I'd knocked on the window to get the driver to stop at an intersection where the road was torn up and traffic was difficult for conventional vehicles.



I stayed in the truck as Coil's men unloaded it.  I sensed some of the people venturing out of their residences, and I was careful to leave them unmolested by the bugs, using only what I had to in order to track them.  Watching from windows and entryways, encouraged by those who left, others ventured to follow.



The area in which I'd ordered the truck to stop was open.  I hoped would encourage the growing crowd to approach.  The truck was parked in the middle of the road, and the boxes were unloaded onto the ground just below the rear of the truck.  I wasn't sure I liked that they were getting wet, but I knew they were at least partially waterproof.  I should have thought to ask Coil for some kind of platform or pallet to set them down on.



It wasn't two minutes before the first people started to arrive.  The first few were kids, no older than ten, gathered in a loose pack, maintaining a wary distance.  The next two groups were families, parents with their kids in tow.  I noted that the group of men who stepped out of an alley were armed, with knives and clubbing weapons hidden under their clothes and in their jackets.  One of them swatted one of the flies I was using to feel him out.  Were they members of the Merchants, or just a band of grown men that had taken to carrying weapons to protect themselves?



I'd known this move of mine would attract people of all types.  If they \emph{were} Merchants, I was okay with that, I'd accounted for it.  Above all, I knew that this offering of supplies would attract the people who were hungry enough to venture out into the outdoors with the oppressive cloud of bugs looming above them.  I would also attract the people who would want to confront me, Merchants included.



As people arrived and some ventured closer to the pile of boxes, one of Coil's workers cast a wary glance over his shoulder, in my general direction.  I should have told Coil's men not to look my way or show any uncertainty.  It would hurt the effect I had hoped to generate.  To dissuade people from taking the supplies, I set a cloud of bugs around the piles of boxes, enough to be obvious without obscuring what was there.   One of the guys with weapons approached anyways, and I had the swarm move towards him, condensing into a dark shape, buzzing loudly.  He backed off.



In this manner, weighing enticement against implicit threat, I managed to keep the crowd in place as it grew to dozens, then a hundred people, with more still approaching, pushing the number closer to two hundred.  Barely a fifth of all the people I'd tried to get in touch with.  I was okay with that.  It was enough to spread the word.



I was taking a risk, here.  Gambling.  It was like betting someone a million dollars that you'd hit a bullseye, when you'd barely played darts before.  It wasn't that I was confident this would succeed.  It was that I really needed that million dollars.



In short, I needed to get underway with Coil's agenda, and I needed to do it fast.



More people were still making their way towards us, joining the crowd.  The bystanders would be getting more confident with numbers at their back, and they would be getting increasingly worried that if the crowd grew too large, maybe they wouldn't get any supplies for themselves.  If I put it off any longer, they could mob us, and I didn't want that.



No, my gut told me this had reached the point where I had to act.  From my seat in the truck, I drew my bugs together into a humanoid shape, and had the figure approach from the rear of the crowd, walking towards me.  I waited, my attention focused on my swarm's senses.



There was a gasp, then a general murmur.  A woman shrieked.  I felt the crowd part, heard the shouts.  They'd noticed the figure I'd created with the swarm.



Most eyes would be on it, now.  I scattered its shape and had the swarm leap or shoot towards the rear of the truck in a loose blob, arcing slowly through the air to land at the rear of the truck, on top of the crates.



The moment I knew the crowd would be unable to see, I stepped out of my hiding spot and into the midst of the swarm.  I scattered the bugs explosively, sending every one of the bugs flying or crawling directly away from me, revealing myself.  The people closest to the pile of crates I was standing on backed away.



To the crowd, it would look like I'd just transported myself to the back of the truck and materialized from the swarm.  I hoped.  It was a cheap ploy, obvious to anyone who thought about it.  I was banking on the fact that the swarm I had blocking out most of the sun and the whole dramatic lead-up would help sell the illusion.



I kept the bugs swirling around me, tightly packed together so they would be moving in tendrils and loops.  Like Grue habitually did with his power, I was aiming to use my own abilities to make myself look bigger, more impressive.  It was like a dog raising its hackles or a cat arching its back.



``Some of you know of me!'' I called out, and the noises of the swarm accented the words, gave an eerie, strangely loud echo to my voice.  ``My name is Skitter!''



I looked over the crowd.  So many kids.  So many who looked sick, pale with red cheeks.  Some people were dressed too heavily for this warm weather.  Everyone was dirty and damp, their hair greasy and clothes wrinkled.



My eyes fell on a figure in the back of the crowd, who stood out because she \emph{wasn't} unwashed or wrinkled.  Her white and gray costume had patterns on it in light blue that weren't too different from a circuit board.  She leaned against a power pole, her arms folded, content to watch.  The people nearest her were watching her as much as they watched me.



I'd known I'd attract attention from the heroes.  Still, it was intimidating, a reminder of how fragile this whole thing was.



I swallowed.  I had to be confident.  I lowered my volume a step, relying on my swarm to convey my words for me.  It wasn't perfect, there were parts of speech they weren't good at making, but it worked well enough that I kept at it.  ``I am laying claim to this area!  From this moment, I rule this territory!''



People could have booed or jeered.  I'd been almost convinced they would.  Instead, I heard a murmur running through the crowd.  Battery hadn't budged, but I saw her pressing her fingers to her ear, and her lips were moving.  She didn't turn her head away from me, and I could imagine her staring at me.



``I am not the ABB, I am not the Merchants, the Empire or the Chosen!  I am acting in \emph{your} interests!''



Our group had discussed this, after talking to Coil the other night, and we'd hammered out more details yesterday, passing on the details to the Travelers.  Our methods would vary wildly, but we were all making our bids for territory this morning.  I decided not to mention that.  Let the others arrive at that conclusion themselves.



``I demand no money from you, I do not intend to interfere in your lives unless you interfere in mine!  I do not want to take or destroy what you have!''



I pointed at the crates that were beneath my feet.  I lowered my voice.  ``These supplies are yours, a gift from me to you.  And there will be more, delivered regularly for as long as I am here.  My abilities will mean there will be no buzzing or biting flies harassing you, no cockroaches crawling over you as you sleep.  I am offering you protection, security, and reprieve, for as long as you are my subjects!  All I require is that you obey my rules, so hear me!''



``No gangs will operate here.  Merchants?  Chosen?  I know some of you are in this crowd.  Consider this my declaration of war.  I will not permit you to sell drugs, to hurt my people or steal from them, or to seek shelter in my territory!''



I raised my hand, and the swarm gathered coalesced into a tight mass above me, a vaguely spherical shape, six feet in diameter.



``My bugs can devour a cow to the bone in one and a half minutes.''  I had no idea if that was true.  It sounded good.  ``I have a million eyes to watch you with.  \emph{Go elsewhere.}''



``To everyone else!  If you assist any of these groups, give them food, shelter, or business?  If you sell drugs, steal or prey on people in this area, you lose my goodwill.  You will receive no more supplies, and you will earn my attention, with eyes on you for every waking hour.  That's strike one.  If I catch you doing it again?  I treat you as one of the \emph{enemy}.''



I let my words hang in the air for effect, and to give my audience time to consider what I was saying.  I glanced at Battery.  She wasn't moving to stop me\ldots interesting.



``Each box contains enough basic food rations for four people.  They also have first aid supplies and water filters.  These supplies will keep you going until we can start fixing things and making more basic conveniences available.''



``If you want \emph{more?}  Work for me.  This work does not have to be criminal, for I need people to pass on messages, to act as spokespersons for these neighborhoods, and to clean up or rebuild.  For anyone who \emph{does} assist me, them and their families will have access to some of those foods you miss, to showers and electricity, and generous payment.  You and your loved ones will be dry, clean, and you will have fresh clothes.''



I looked over the crowd.  I could see people getting restless.  At least they weren't lynching me.



``Thank you for listening.  These supplies are yours to take.  One to each family or group, up to two if your family is large enough.''



My monologue finished, I waited.  Nobody ventured forward.  Had I done too effective a job at intimidating them?



I was just starting to wonder what I'd do if nobody moved, when the first man stepped forward, followed immediately by his wife and a pair of kids.  The wife had a very red nose and circles under her eyes that made me think she had a bad cold.  The parents didn't make eye contact with me as they accepted the box that one of Coil's workers lifted down to hand to them.  The children hid behind their mother.  There was no gratitude, nor any thanks given, as the father turned to carry the box of food and necessities back to wherever he was taking shelter.



Seeing the first family leaving with their supplies, others grew brave enough to venture forward.  In moments, there was a crush of bodies.  I stepped onto the back of the truck as the boxes disappeared from beneath me, and I watched the crowd for any violence or fighting.  One altercation began as two men both grabbed the same box.  Before their violent tugging match got them or someone else hurt, I sent a buzzing flurry of bugs in between them.  They dropped the box and backed off, staring at me.  When I didn't move to stop them or do anything further, they each returned to the pile to scrounge up different boxes, leaving the other on its side in the water.



There wasn't enough in the way of supplies.  I could see the atmosphere shift slightly as people realized it.  There were too many people present versus the amount of boxes Coil had provided me, even with one box serving a whole family.



I knew Coil had more – his underground base had stored ridiculous amounts, so he had access to a supplier, or he \emph{was} the supplier.  I began formulating a plan, figuring out how I'd get boxes to those who were walking away from here empty-handed.



I was interrupted from my thoughts.  A man shouted, and I saw the crowd backing away.



It was one of the men who'd had a weapon.  He'd drawn and swung a crude knife to ward people off and grinned maniacally at the reaction he was getting.  The scruff of beard on his chin was white, but it seemed rather premature given his apparent age.  He was shirtless, with a long sleeve shirt tied around his waist, and scratches crisscrossing his upper body.  His buddies stood back, smirking and grinning.



It was a bad judgement call to pull this right in front of me, but I supposed people were at a point where they weren't at their most rational.  That, or he was high on something.  I could see him as a member of the Merchants, either way.



``Big man,'' I called out, ``You feel proud with that knife of yours?''



He turned towards me, ``Fuck you!  I'm not scared of \emph{bugs}.''



I stepped down from the back of the truck.  People backed away, but the man held his ground.  As I got closer, I saw how his eyes were too wide, and he chewed his lip like it was trying to get away from him.



``You a member of the Merchants?'' I asked.



``Fuck you!'' he snarled.



I wasn't going to be able to have a conversation with this guy.



``Fine.  Don't care.  You're threatening my people?  You'd better be ready to take me on.''



``Not scared of you!''



I shrugged, ``Prove it.  Use that rusty thing on me.  Stab me.''



He looked around at the crowd, hesitated.



``What?'' I asked him.  ``I thought you weren't scared.''



``I'm not!''



``Then stab me!'' I raised my voice, shouted at him.  ``Or are you just a bully, getting weak in the knees when you're facing someone that stands up to you!?''



He made a motion as if he was going to lunge for me, then stopped.



``Pathetic,'' I snarled.  Not for the crowd.  I said it for him and him alone.



He lunged, holding the knife with both hands to drive it into my stomach, just beside where I had the armor.  I resisted the urge to bend over, but I did have to step back for balance, and I had to put my hands on his shoulders to steady myself.   I clutched his shoulders, digging my nails in for grip.  I could feel pain radiate from my stomach and into my lower abdomen and chest.  That was despite the fact that the fabric of my costume had kept it from piercing my flesh.



I forced myself to stand straighter, still holding his shoulders.  He stabbed again, but it was ineffectual.  Knocking one of my hands from his shoulder, he used the space that gave him to slash at my throat.  The first hit had hurt because of the force of the charge behind it, I could almost ignore these follow-up strikes.  He stepped back and looked at his knife, confused.  I hadn't gone down.



I extended my arm and let the bugs flow from beneath my costume in one swift movement, like water poured from a cup, covering him.  The crowd backed away as the man began screaming incoherently.  He threw himself backward into the inch-deep water and rolled around like he was trying to put out a fire.  Maybe he was – the bugs I'd set on him were laced with capsaicin.



As his thrashing continued, I waited patiently, watching.  As he used one hand to prop himself up in a crawl, I stepped forward onto his knife hand.  My heel settled on his knuckles, and after I'd readjusted my footing, I ground it down, letting most of my body weight rest on that heel.



The volume of his screams increased.  As I lifted my foot, he moved his hand, rolling onto his back to clutch at it, dropping the knife in the process.



I bent down to pick up the blade, and when I stood up again, Battery was ten feet in front of me, one pace closer to me than any of the rest of the crowd that ringed me and the Merchant.



``I can't let you use that,'' she gestured towards the knife.  There was a faint glow from her costume.  I gathered she was charging up her power.



``Wasn't planning on it,'' I lied, swarm buzzing in sync with my words.  I'd considered stabbing the guy in the hand or somewhere where it wouldn't be terminal, but hadn't been certain on the route I would go.  I reversed the knife and gently lobbed it towards her.



She spent the accumulated charge of her power and caught the knife out of the air by the handle. ``How does this tie into the stunt you helped pull at the HQ?''



``The Wards' building?  The intel we got from there was valuable, and that kind of money buys a lot of things.''  I looked at the remaining pile of supplies.  The majority of the crowd had stopped collecting their boxes to watch the fight with the Merchant and my exchange with Battery.



As if noting what I was looking at, she glanced at the crowd encircling around us.  ``I don't agree with this.''



``But you're not going to stop me, and you're not going to try and arrest me, despite what happened the other night,'' I answered her, ``Because I'm the lesser of a whole lot of evils that are in the city right now.''



``Mm.  \emph{For now}.''



``For now.  Until then, I've got supplies from an outside agent, I'm not stealing them from the same sources you guys use, and I'm getting them out to these people at my own expense.  I'm policing this area until the police can get back to doing it themselves, and I'm dealing with people who need to be dealt with.  You're not about to get in my way, are you?''



Battery surveyed the crowd again.  ``What's your agenda?''



``Do I have to have one?''



``Yes.  Your kind always has an agenda.''



``Maybe I'm unique.''



``No, knowing what you tried to pull with pretending to be a villain?  Or pretending to be a \emph{hero} that's pretending to be a villain?  You're more likely to have some scheme at play than anyone else.''



I sighed.  ``Don't know what to tell you.  No agenda.''



She frowned, ``When we first set post-Endbringer measures in place, your team was listed as low priority, and we were instructed to ignore you.  Too costly in time and resources.  I suspect someone intended to change that after your little stunt the other night, but the memo hasn't gone out yet.  You hear me?''



I tilted my head in a small nod.



``So I'm going by the book, and I'm walking away.  \emph{But} I'll be keeping an eye on you, on this, and the moment you go too far, we're coming after you, no holds barred.''



``I wouldn't expect any less,'' I answered her.



With that, she disappeared in a blur, the water parting in her wake.



With her gone, the rest of the crowd swooped down on the remaining supplies.  People maintained a respectful distance, but oddly enough, they weren't acting as scared of me as they'd been before I attacked the Merchant and before I'd talked to Battery.



Had her leaving me alone given me a measure of legitimacy?  More importantly, had it been \emph{intended} to give me legitimacy as ruler of the area?  She hadn't needed to step in right then.  Probably.  I had to admit I wasn't sure if I would've gone through with stabbing the guy.



``Listen up!'' I shouted.  I used my swarm to give me more volume, and to stand out against the noise of the crowd.  People went silent, and every set of eyes turned towards me.  I stepped up onto the truck, hiding myself briefly in the swarm as I hopped up.



I addressed them, ``Not everyone will get a box today.  That is not an excuse to take what others have already claimed.  As I said, I will \emph{not} tolerate stealing or theft among you.  If you try it, I'll treat you the same as I treated \emph{him}.''



As I pointed, the crowd parted slightly to reveal the Merchant who was still crawling away, simultaneously struggling to douse himself in the one or two inches water on the street and to crawl with three limbs – he was favoring the hand I'd stepped on.  His buddies were gone.  They'd left him.



``If you do not get a box, \emph{stay}.  I want the head of each family or group to raise their hands.  This will help me ensure you get something before the day is over.''



It took a minute before the last of the boxes were claimed.  There were some resentful looks as the last of the people left.  I had thirty or so remaining people, and after some brief discussion, seven of them raised their hands.



I concentrated on the swarm, and found a collection of ladybugs.  I piloted a group into each set of raised hands, and watched as people lowered their hands to look.



``Each of you now has three ladybugs in your hands.  Keep them, and I will use them to find you later today to drop something off for you, with a small gift to each group of you for being patient.''



Slowly, they began to peel away from the group and leave.  I began letting the swarm disperse, but I used the fact that I had the bugs all together to direct a mass towards my lair.  The cream of the crop – the good ones.



As Coil's men got back in the truck, my swarm-sense told me that one person had stayed behind.  I turned to get a better look at her.



She was twenty or so, and her red hair had been set into long dreadlocks that she must have been growing for years.  I wasn't sure on the effect – white people didn't grow good dreadlocks.  She wore rain boots, a calf-length skirt, and had a colorful bandanna around her forehead.  She was pale, and she fidgeted nervously, not making eye contact.  High or afraid?



Then she saw I was looking and she met my eyes.



``Yes?'' I asked her.  ``You've got the ladybugs.  I \emph{will} get you a box.''



``No.  It's not that.''  She looked at her hand where the ladybugs were.



``Then what is it?''



``You said we were your people, that you were protecting us.  Does that mean you're going against the other groups?''



``Yes.''



``My kid brother.  I- \emph{he} needs help.  My parents are sick and they're in the hospital and I can't tell them because I told them I'd take care of him, um, and I asked the cops but they're so busy and there's no way they can help, and I was going to ask that hero, Battery, but then she \emph{disappeared} so \emph{fast}--''  The words spilled out of her mouth, less and less intelligible as she kept talking.  She only stopped when her voice cracked.



Breathing hard, out of breathlessness or emotion, she stared at the ground, clenching her fists.  I could feel one of the ladybugs get crushed in her grip, fading out of existence as far as my power was concerned.



``Stop,'' I told her, without using my swarm to change my voice.  ``Breathe.  What happened?''



She looked up at me, then she swallowed hard.



``The Merchants took him.  My kid brother.  I want you to get him back.  \emph{Please}.''



