





I sat cross-legged in my chair on the second floor of my lair.  A mug of tea was warm in my hands, and the room was dark.  Only a faint light filtered in through the slats at the top of the metal shutter that covered the window.  My mask rested on one knee.



My attention swept over my territory, with an emphasis on the centermost area near where I'd held my speech.  The reach of my power wasn't quite good enough to extend to the outer edges of my territory, which left me anxious.  I was craving one of those moments when my power would go into overdrive and increase its range.  Minutes passed as I followed my `subjects' and did what I could to get to know them.  My bugs remained on the backs of people's elbows, at the small of their back, and I'd maybe put a small fly in their hair if it was long enough that they wouldn't feel it.  Not enough to bother anyone, or that anyone would necessarily notice, but enough for me to track their movements.



Two groups arrived within a minute of one another, each at different points of my territory.  Thirty-two people in all, with eight in the first group and twenty-four in the other.  Both groups reacted, jumping and backing away as my swarm swept over them.  I could feel the vibration in the air as one in the second group laughed.  The others joined him.  I'd held off on attacking, just using the bugs to get a headcount and a sense of who was there.  There were men and women, young and old.  Each of them had weapons of some sort, and fifteen in total had guns.



The Merchants were responding to my bid for control.  Good.



I sipped my tea and found it was lukewarm.  I took big gulps in the hopes of finishing it before it got cold.



One of the Merchants in the first group shouted something, loud enough for it to carry down the street, and fired a gunshot.  Impulsively, I tried to tune into my bug's hearing and interpret what he was saying, but the strangeness of the noise stopped me.  It didn't translate from a bug's `ears' to mine.



The first group started running down the length of the street.  They scattered, with smaller groups of two people each heading to different buildings.  Finding the windows boarded up and the doors locked or barricaded, they started tearing at the plywood and planks.  Some struck at the doors with their improvised weapons.



There were people inside two of those buildings.  Not many, but still.  Those were \emph{my} people.



Using my swarm on them would have been easy, but this wasn't just a question of taking the Merchants down.  I needed to do it so effectively and undeniably that they would hesitate to come back.  If I did it well enough, ideally, word of mouth would help keep others from trying anything similar.



Why did that line of thinking sound so familiar?



It dawned on me: Bakuda.  She'd said something similar when she'd been doing her monologue and pretending to be the new leader of the ABB.



Well, that was disquieting.



Still, my reasons were different.  I wanted to protect my people.  Bakuda hadn't been motivated by an interest in anyone but herself.



I dismissed that line of thinking and gathered the swarm into a vaguely humanoid shape with a head, arms, and a torso.  I tried to balance it on two columns like legs, but I erred in favor of dissolving that into one column for the lower body over risking having it fall over.  A good thing the ground was mostly dry, there, or I would have required far more bugs to maintain the shape with the lowermost critters constantly drowning or being pushed away by the motion of the water.



I piloted the swarm-figure slowly towards the first group.  Someone noticed and turned away from the door he was trying to smash down with his makeshift club.  He shouted and laughed, drawing the attention of others.



Running forward, he swung the club at the swarm like he was trying to hit a home run.  The head was scattered, dashed to pieces, and he laughed again.



Until the rest of the swarm dogpiled him.  Then he started screaming.



Roughly half of his `friends' laughed at him.  Lots of laughter.  Were they all on something?  The remaining four people hurried to his side and tried to claw the masses of bugs away from him.  As they got bitten and stung in retaliation, they backed away, brushing the bugs off of their arms and legs, leaving him to his fate.



The bugs I had in the area coalesced into another vaguely humanoid shape.  Then another.  In moments, I had a half-dozen figures in a loose ring around the group.  I moved them forward, and my enemies backed away from them.  I used this to herd the Merchants until they stood back to back in a tight circle, surrounded.  They had their weapons raised, but they had to know how ineffectual the baseball bats and guns would be.



Then I waited, keeping the swarm-figures remaining as motionless as possible.  If it weren't for the man still thrashing on the ground, screaming, it would have been eerily still and quiet.



The second group was oblivious to the events a few blocks away as they roamed through my territory.  A woman in the group was singing, loud enough that her voice would be carrying to nearby residents.  She was letting them know that trouble was near.  I noted that she was holding a plastic tank of gasoline, if the topographic map I was getting from my swarm-sense was right, and the box in her other hand could easily have been matches.  That wasn't good.



Still, her group had yet to do anything.  I kept an eye on them and waited.



Someone in the first group made a run for it, rushing for the space between two of the swarm-figures that surrounded his group.  He didn't make it.  The swarms both intercepted him, and he went down, howling in pain.



Unease gave way to panic as the group realized they were trapped.  A woman shoved a man into the nearest swarm, trying to use him to clear the way, but she only got two more steps before the wasps, black flies, mosquitoes and hornets caught up to her.  She violently swung her arms around herself in a futile attempt to fight off the bugs, and succeeded only in throwing herself off-balance and falling to the ground.  The spiders, ants, centipedes, millipedes, beetles and all of the other crawling parts of the swarm rolled over her, burying her beneath their mass before she could stand.



The remaining four Merchants in the first group exchanged muttered words, some kind of plan.  Then three of them broke for it, each headed in a different direction.  I wasn't sure what outcome they expected.  A mass of bugs caught each of them, and they all went down, limbs flailing, screaming.



That left only one.  He dropped into a crouch, his hands on his head, and looked frantically around for some kind of escape route.



So I gave him one.



The swarm-figures parted enough that he had a chance to retreat.  It took him ten seconds to notice it, and another few seconds to build up the courage to make a run for it.



He bolted.  Seeing the general mass of insects down the road, he decided to turn into a series of alleyways.  I let him run for a minute.



He was halfway down an alley when I drew the ambient bugs from the vicinity into a loose humanoid shape, not as dense as the others.  Still, seeing it stopped him in his tracks.



He turned to retreat the way he'd come, only to find another swarm coalescing into a second figure at the other end of the alley.  His head whipped around as he realized he had no escape routes left, and then he screamed, a primal, despairing sound.



The swarm figures moved towards him at a glacial pace, with more bugs joining them every second, to give them more mass and more raw attacking power.  His composure cracked before they even reached him, and he charged headlong into the swarm that had been at the far end of the alley.  Bugs tore into him, pinching and stabbing him, and he made it nearly to the edge of my power's range before his legs buckled.  He landed on top of a pile of the trash that the nearby building's residents had been stacking in the alleyway, and the swarm started mauling him.



Group one down.



I finished my tea, then made a face.  The teabag had leaked grit, and some had settled into the bottom of my cup.  Bitter.



I put the empty cup down at the base of my chair, and then I turned my attention to the second group.



\sectionbreak



I didn't even need to think about it.



``I'll do it,'' I told the redheaded girl with the dreadlocks.



She looked surprised.  Odd.  She'd asked me, but she hadn't expected me to help?  Or had she expected me to demand something from her in exchange?



Should I have demanded something in exchange?



``Stay here.  I'll be right back,'' I said.



I turned and walked to the front of the truck, knocked, and the driver popped the door open for me.



I spoke in a low voice, ``We're done here.  Tell Coil I need more supplies.  Seven cases at a minimum, by the end of the day.  And tell him I think you guys did a good job, so if he's up to giving you any kind of bonus, it would be a good time.''



He gave me a tight nod, then closed the door.  The truck drove off, leaving me with the girl.  I approached her, and I could see the effect I was having on her.  She was unwilling to meet my eyes, and her fidgeting stilled as I turned my full attention to her.



``Your name?''



``Sierra,'' she answered me.



``Let's walk, Sierra,'' I said.  ``I need details if I'm going to help.  The more you can tell me, the better.''



She joined me as I headed towards the sidewalk, and after taking a moment to compose her thoughts, she started telling me what had happened.  ``Three weeks ago, everything was so normal.  I was finishing up at college.  Bryce, my brother, went to Arcadia High.  My uncle was staying with us because he was down on his luck, as my dad put it.  I'm almost positive it had something to do with his drinking.''



I nodded.



``Then Leviathan came.  The sirens woke us up early in the morning, we hurried to the shelter, and by the time it was midday, we were standing in front of what used to be our house.  Flattened, everything we ever owned was gone.''



``I'm sorry.''



From the look on her face, it seemed like I'd surprised her again.  What kind of image did she have of me?



``Thank you.  We- we stayed in a family friend's basement, and they had another family there as well, on the upper floors, so it was crowded.  But it was better than the shelters, or so we thought.  My dad, my uncle and I worked with one of the cleanup crews.  Trying to get things normal again.  Until word got out that one of the crews had been attacked, the women assaulted.  Um.  So they told me I couldn't work with them.  I worked for one of the shelters instead.  Handing out sheets, making beds, keeping track of names and passing on requests for stuff like insulin or other meds that people needed.  Long hours, thankless\ldots''



She put a hand to her face, ``I'm rambling.''



``It's fine.  Better that you give me too much information than not enough.  Keep going.''



``My uncle got sick fast.  He had a cold just days after Leviathan came, and it got complicated after, became pneumonia.  The hospital sent him out of town for medical care, and we got word he'd died just two days after that.  Respiratory distress or something.  Drowning in his own lungs.  Less than a week from the time he got the cold to the time he died.''



She stopped talking, and I didn't push her, giving her time to compose herself.  Had she been close to her uncle?



``By the time we heard the news, Mom and Dad were sick too, and Bryce was showing symptoms.  It wasn't a cold.  It was more like the flu, but with what happened to my uncle, we didn't want to take any chances.  None of them could keep anything down, sinus problems, pounding headaches, tired\ldots we went to the doctors and they said it could be toxic mold exposure.  The moisture, always being cold and damp, and not having enough to eat, being in that basement, with the foundation possibly cracked or the mold disturbed by the vibrations and damage in the attack\ldots Um.''



I wondered if this was pertinent to what happened to her brother, or if she was just really wanted someone to talk to.  I didn't want rush her, but I did try to get her on track,  ``So your parents and brother got sick.''



``And I was left alone.  I guess I was saved by the long hours at the shelter, I wasn't spending half as much time in the house where they got exposed to the mold.  I had to find a new place to stay.  A guy from the shelter heard my story, offered to give me a room in the church.  Near here.  I was grateful, I took it.  My brother got out of the hospital, and he came to stay with me.  He got the cot, I got the floor.  A day and a half later, they came.''



``The Merchants?''



She nodded.  ``They attacked the church.  Nine or ten of them.  We outnumbered them, but they had weapons, and they caught us by surprise.  One of them threw a molotov cocktail through a window.  There were other families there, families with kids, so I grabbed a fire extinguisher and tried to stop it from spreading.  Spraying around- I couldn't put it out, didn't want to try in case I just spread it around, so I just contained it, for all the good it did.''



She shook her head, ``They came through the doors and began attacking people, one of them grabbed my brother, I- I panicked.  I used the extinguisher to spray towards them and tried to pull him away.  I couldn't, and others were approaching, so I left him and I escaped through the broken window where the bottle had been thrown inside.  When I got back an hour later, there were fire trucks and police and ambulances there.  My brother was the only one missing.  The others were there, but badly hurt.  Burned or cut up, beaten.  Derrick, the man who'd invited me to stay there--''



She broke off, and she stopped walking, turning away so her head was facing away from me.



I waited patiently.  When she'd turned back so I could see her face and started walking again, I gently asked, ``Dead?''



She shook her head.  Quietly, she said, ``They cut him up with a broken bottle.  The doctor said they bent him over and shoved it between- he'll have a tube running out of his stomach and into a bag for the rest of his life.  And he might never walk again.  You understand?''



``I think so.''  Not that I wanted to.



``Not about what they did, I mean, do you understand what I'm saying about these assholes, these\ldots I don't even have words to describe them\ldots to say how much I hate them.  God!''



``Keep going,'' I urged her.



``I don't know you.  I barely know about you.  I heard something about you in some bank robbery around the time I had exams--''



``That was me.''



``I don't know how you operate.  I don't know your methods, outside of what I just saw back there.  But I want you to know that I've always considered myself a pacifist.  I've never been in a fight, I've always tried to stand up for people and give them the benefit of a doubt, to be fair and never do anything to hurt another person, even with words.''



``Okay.''  How long had it been since she slept?  I was having trouble following her train of thought.



``So I think it should mean something extra, something \emph{special}, when I'm telling you to hurt them.  Fuck them up.  Hurt them as much as you think they deserve, then \emph{double} that.  \emph{Triple} it, just- just make them--''



She stopped yet again, choking on her words.



I had a hard enough time keeping afloat in a conversation when I was Taylor.  How was I supposed to do it as Skitter?  What was appropriate, what was expected?  I hadn't figured any of this out, yet.



I put a hand on her shoulder, and she flinched.  I left the hand there, and I measured out my words.  ``Trust me when I say I have that handled.''



She looked at me, and I gave her a small nod.



``God,'' she muttered.



``Tell me more about them, and tell me anything about your brother that might help me identify him.''



She startled, as if shaken from a daydream.  She reached into her pocket and handed me a folded picture.  It was hard to pin down the kid's age.  He was skinny in a way that suggested someone who was going through a major growth spurt but hadn't yet filled out.  He had large, blue eyes and a snub nose.  There wasn't a hair on his face, and his black hair was spiked so the top stuck up in every direction.  Like so many guys, he didn't seem to know how to style his hair.  He ignored the sides and back in favor of overdoing the parts he could see when he looked in the mirror.



The boy could have been a tall eleven year old and he could have been a young-looking sixteen.



``Bryce?'' I asked her.



She nodded.  ``Bryce Kiley.''



``Is there any chance he escaped?''



``No.  I've checked all the usual places.  His friends, our old house, what's left of it.  I stopped by the hospital where Mom and Dad are, and the nurses say they haven't seen him.''



``How long ago did he disappear?''



``Two days ago.''



I nodded.  I vaguely recalled that the forty-eight hour mark was when police considered a missing person as good as gone.  That didn't mean I wouldn't try.  It also meant I could feel less guilty about handling things here, with my territory, before starting my search.



``Did you get a look at the people who took him?''



``Some.  The one nearest me, he was fat, white, and he had one of those bushy wild man beards.  You know the kind I mean?  It sticks out everywhere, no grooming--''



``I know what you mean.''



``And his hair was really long and greasy, so it stuck to his scalp.''



``Okay.''



``Then there was one woman.  Maybe middle-aged, bleached blond hair.  Trailer trash.  And she was with this tall black guy with a scar on his lips.  He was the one who was grabbing Bryce.  He had a bottle in one hand he was drinking from and a length of pipe in the other, so I think he was the one who used the bottle on Derrick\ldots''



``Were they wearing anything?''



``I don't think anything major.  Um, most of the guys were shirtless, and the ones who were wearing clothes were wearing t-shirts, some with no sleeves or with the sleeves torn off.  Oh.  And a lot of them had these bands around their wrists.  Plastic, colored, sometimes one or two, but the black guy had a lot.  I remember seeing the ones on the black guy's wrist, and thinking it didn't seem like something he would wear on his own.''



``Ok, that last bit is especially good.''  Were they a way of marking status?  More bands for higher status, with different colors meaning different things?  ``Anything else?''



``I can't think of anything major right this second.''



``Okay.''  I thought.  But she might come up with something more?  ``Where are you staying?''



She hesitated to answer, but she finally relented and admitted, ``Nowhere.  I was out all last night, looking.  I was going to go back to the place we'd stayed at first, our family friend, but\ldots''



``The mold problem, and you said it was crowded.  That won't do.  You'll come with me.''



Concern flickered across her face.  ``I don't know--''



``It's better if you're close, so you can answer any questions I have and so I can keep you informed.''



She frowned, and I could practically see her working to think of a way to get out of my offer without offending.  I knew if she didn't come with me, she'd probably wind up searching for a mediocre to unsatisfactory place.



``This isn't really negotiable,'' I told her, just to forestall any excuses.



For her part, she didn't argue.



We made our way to the beach, and after I'd checked both ways, I led her into the storm drain.  It took some urging to get her to enter the darkness, and I had to grip her hand to lead her into the oppressive black.  I unlocked the barred door that led into the cellar and locked it behind us.



When I flipped the switches to light up the ground floor, her eyes went wide.  ``You have power.  Erm, electricity.''



``And running water.  Stay here a moment.''  I took the stairs two at a time to get to the second floor.  Nothing too sensitive there, but I did walk up to the stairs leading to the third floor and slid a panel across the stairwell.  With my keys, I locked it in place.  I didn't feel it was that obvious to anyone glancing around the room.  It looked like a section of wall until you saw the keyhole.  I verified the bugs were all locked up tight in their individual compartments in the lids of each terrarium, then headed back to Sierra.



``I'm making tea,'' I spoke, as I came down the stairs.  ``You want some?  Are you hungry?''



``I'm not a tea drinker, and I haven't had it in years, but that suddenly sounds like the best thing in the world.''



``I'm afraid I don't have a kitchen table or chairs or even a living room for us to have the tea.  There're beds in the other room, if you want something to sit on, and you can make yourself comfortable there.''



``This is strangely domestic for a villain.''  I turned to look at her and she hurried to add, ``I mean--''



``It's fine.  I'm not offended, I \emph{am} a villain.  But I'm also a person under this mask.  Someone who prefers tea to coffee, who enjoys reading, who\ldots''  I floundered.  ``\ldots{}likes sweet and savory foods but dislikes anything spicy or sour.  Point being, I'm someone who wants to make sure \emph{you} get taken care of.  Especially if you're among the people I'm protecting in the territory I'm claiming.  Go.  Find a bed.''



Obediently, she went to do just that.



I put the kettle on, then got the sugar.  What did I have that would go well with tea?



I got out a box of graham cookies with chocolate on one side.  I poured out the tea into mugs and put a teabag in each.  I poured milk into a small measuring cup so Sierra could have milk with her tea if she wanted, and similarly doled out sugar into a small bowl and placed a spoon inside it.  Then I tore open the box of cookies and sorted them onto a plate.



I put everything onto a tray and went to find the room where Sierra would be seated.



She was lying on the bunk bed, already fast asleep.



Quietly, I set the serving tray down on one of the luggage trunks at one corner of the room, collected my own tea and went upstairs to the second floor.



\sectionbreak



It took me three tries.



On the third attempt, the beetle, supported by others and a crack in the pavement, successfully struck the match against the side of the box as the other bugs adjusted its position.  A small flame flared at the end.



Other bugs leveraged matches out of the box the woman had dropped, gripping the matches in their mandibles, sometimes two or three bugs to one match.  Like a relay, they touched one match to another, passing on the flame from the beetle's match to each of the others.  It wasn't long before there were more than thirty beetles each with a lit match in its mandibles.  Some died from the heat their own matches generated, but most were able to stand it.  I could imagine the visual of it; kind of like a small sea of tiny flames like lighters at a concert.  Or maybe it was closer to a lynch mob, a crowd holding torches, radiating with an imminent threat of violence.



It was a shame it was closer to noon than midnight.  I imagined the effect would have been even more exaggerated in the darkness.



The woman stepped away, pulling off one of her wet shoes.  She threw it at the bugs, and it rolled over a few.  A heartbeat later, it burst violently into flame.  It didn't make a difference.  The swarm that was armed with matches was already too spread out for one shoe and one small fire to slow them down at all.



The woman's attempts to remove her other shoe made her fall over, and she suppressed a grunt of pain as she landed.  She successfully kicked off her other shoe, and then began simultaneously fumbling with her belt while trying to crab-walk backwards away from the advancing sea of tiny flames.



I could picture it.  It would be intimidating:  A sea of bugs acting with a backing of human intelligence, each with their tiny torches.



Doubly intimidating if a swarm of bugs had made you drop and spill a can of gasoline onto your shoes and the cuffs of your pant legs.



She successfully undid her belt, then began trying to remove the tight-fitting jeans she wore.  The woman got as far as getting her jeans around her ankles before she got stuck.  Some beetles and roaches took to the air, carrying matches to the ground behind her, cutting off her retreat.  She screamed at the others in her group, but nobody leaped to her assistance.



A beetle fluttered forward and touched a match to her jeans.  In an instant, the bundle of cloth at her feet was on fire.



She tried to pat it out, but her efforts to remove her shoes had gotten trace amounts of gasoline on her hands.  Her right hand ignited, the insects on it dying, and she threw herself to one side to thrust it into a hole in the road where water had collected, her feet still kicking as she tried to remove her jeans.  Gasoline transferred to the water's surface and flickered with the faintest of flames.



One of her friends finally stepped forward to help her, grabbing her under the armpits and dragging her ten feet down the road to a spot where more water had collected.  Together, they worked to put out the flames, dousing her bundled jeans into the water.  I could maybe have stopped him, driven him away, but my interest was more on spooking them than causing grievous physical harm.  I wouldn't lose much sleep over burning her with the things she'd intended to use on others, but I wouldn't stop her from putting herself out.



Apparently seeing the woman get set on fire by the swarm had done its job in unnerving my enemies.  The group scattered, and I let them run.  One by one, I took them down by creating the human shaped swarms and then attacking them.  Some fought, others ran, but each of the Merchants succumbed eventually, choking on the bugs or losing all self-control in the face of the pain the attacking swarm inflicted.



The human shapes were less efficient than a regular swarm, but I imagined the psychological effect was that much greater.  A swarm of bugs was something you could encounter any day.  An uncannily human figure that you couldn't hurt with any conventional weapon, who threatened incredible pain if it got close enough?  It was something my enemies would remember, and it was something they could tell others about.



I gathered the swarm into a figure that stood next to the woman with the burned feet and her friend.  I drew more and more bugs into the swarm, bloating it and drawing it up to the point where I couldn't make it any larger, without the bottom half giving way.  I gauged it to be somewhere close to twelve feet in height.



Then I let it fall on top of them.  That polished off group two.



I stood from the armchair, stretched, and pulled on my mask.  I bent down to pick up my mug, then headed downstairs to check on Sierra.  She was still sleeping, but I'd known that.  I'd felt secure about removing my mask only because I had bugs on the girl, to keep track of her.  I'd know the second she stirred.



I went into the kitchen before sending a text to Coil:



Merchant burn victim & other wounded near Sandstone & Harney.  Send medic?



No use having the woman die from any complications from her injuries.  Besides, maybe he could get her to offer up information in exchange for her freedom.



I dialed Lisa next.



``Hey, Boardwalk empress,'' she answered me.



``Tattletale.  How's it coming?''



``It's not.  I'm gathering intel on the enemies in my territory.  A few have migrated my way in response to what the rest of you are doing, regrouping.  I'm trying to see if there's any useful tidbits of info I can pick up, and if there's maybe a way to fuck with all these guys at around the same time, so they know there's nowhere left to go.  In the meantime, I'm helping Grue out, figuring out where he's got Merchants hiding in his area.''



``He's doing okay?''



``No problems, last I heard.  You?  I saw that cloud of bugs earlier.''



``Made a big play.  Everyone here should know this is my territory, now.  Merchants tested the waters, I dealt with it.  Remains to be seen if this works out in the long run.''



``Hmmm,'' she replied, ``I'm getting the impression you're a little further along than the rest of us.''



``If that's the case, then that's great.  I want to be in Coil's good books.''



``I want you to be too.  You know I'm here to help if you need it.''



``Yeah.  That's why I'm calling, actually.  I need to find someone.''



``Do tell.''



I gave her the rundown on everything Sierra had told me.  She stopped me when I got to the bit about the armbands.



``Those aren't for rank,'' she informed me.  ``But you're not wrong in saying they're like status.  They're more like\ldots boy scout badges.''



``Boy scout badges?''



``From what I can gather, you get one for attending one of the Merchants' `events'.  Colors are supposed to represent what the each one was about.  It translates to a kind of respect, showing you're loyal, whatever.''



``I'm not sure I understand.''



``And neither am I, to be honest,'' she replied.  ``And that bothers me.  So in the interests of getting intel and maybe getting a lead on this missing boy of yours, do you think you could get away from your territory, tonight, to join me in figuring this out?''



``I don't want to leave just yet.''



``Merchants are throwing a big bash tonight, so I doubt they'll be attacking your territory.  In fact, I'm wondering if they were attacking your territory to get cash or stuff to barter at the event as much as they were responding to your claim.''



``Maybe.''



``And Chosen aren't a threat right now?  They haven't said or done anything yet?''



``Not yet, no.  Haven't run into any.''



``Grue and Imp are probably going to want to wind down and go on the defensive later today.  You can have one of them babysit your territory if you're worried.  You have no good reason to refuse.  Come on, let's go see what a Merchant's party is all about.''





