





Coil had put Bitch's hideout in an area nobody wanted to be, masked with the appearance of a building nobody sane would want to enter.  Grue's place and my own lair were camouflaged in outward appearance and set in more discreet locations.  Tattletale's place, by contrast, was in plain sight, and it was also one of the highest traffic areas I'd come across in the past few days.



The city block that hosted Tattletale's hideout was a short distance from Lord street, and it sported only two intact buildings.  The first building was a gas station that was currently hosting more than a dozen wrecked or flooded cars that had been dragged off the road.   The rest of the area had lots where buildings had once stood, each bulldozed clear of the rubble that had been left in the wave's wake and surrounded with sandbags to keep the water from pouring in.



The second building was a sort I'd seen often enough as of late.  I'd stayed in similar places for nearly two weeks before rejoining the Undersiders.  The structure stood in the center of the area, surrounded by tents and communal areas that were sheltered by tarps set over metal frameworks – a dining hall, a medical bay, portable washrooms.  Each of these outdoor stations had dozens of people gathered around them.  It was a shelter.



She'd told me not to dress up, so I hadn't.  She'd also told me not to wash my hair today, but it was too late for that.  I'd donned a brown spaghetti-strap top, rain boots and a pair of lightweight black pants that were a little worn from the past few weeks, but had the benefit of drying quickly.  My knife was tucked inside the waistband of my pants, at my back.  Not obvious, not entirely hidden either.



Way things were these days, cops were letting things slide as far as concealed and openly displayed weaponry went.  People needed protection, and so long as the armed didn't break the rules about using the weapons on people who didn't attack them first, most people wouldn't give them much trouble.  Some shelters wouldn't let you in with a weapon, of course, but some did, and others disallowed firearms but let other weapons slide.



I made my way inside, joining the rest of the crowd.  Cots filled the majority of the building's interior, and both possessions and people made navigating between the beds difficult at best.  Signs were spread out over the walls, some professionally made, others written in plain print with permanent marker:



\emph{`Priority Order: Sick, injured, disabled, old, very young, families.' } In smaller print below was the message, `\emph{Please be courteous and give up your places to priority individuals.'}



\emph{`No pets'} was written on a square of white cardboard in permanent marker and triple underlined.



\emph{ `Abuse or threats directed at staff or other residents will NOT be tolerated.'}



\emph{`Belongings go under your cot.  Excess + mess may be removed from the area.'}



\emph{`No smoking within 30 paces of facility}` was printed on a professionally made sign, but the line that was scrawled beneath in permanent marker was not: `\emph{there are sick people here!'}



I found a big, burly guy that wore an orange vest and name tag and approached him.  He was talking to someone else, so I waited.



When he turned to me, he frowned, ``You wanting to stay here?''



``No, but--''



``Opened our doors yesterday, and we're already nearly full.  Any more space is reserved for priority people.  If you want a place, you can try the other shelters down--''



``No.  I have a place.  I'm just looking for Lisa.''



``Works-here-Lisa or Staying-here-Lisa?'' he asked.



``Both?'' I guessed.



``Front desk.  If she's not there, wait.  She'll probably be in the back getting something for someone.''



I headed to the front desk where a crowd of people had gathered.  The desk itself was a simple construction of unpainted, unvarnished wood.  The people were wet, dirty and didn't look to be in the best of health.



Lisa was at the end of the front desk furthest from the front doors, wearing the same orange vest and name tag the other staffer had been.  Her hair was in a french braid, with a few strands hanging free.  She was talking to a woman who might have been fifty or sixty.  A large black and white map of the city had been stapled to the wall behind the counter where Lisa was working.  Colored pins marked various spots on the map, and areas had been outlined and shaded in with markers and highlighters.  Words were written in the boundaries of these sections.  Many areas were marked with yellow highlighter, with the words `Merchant Territory: Very Dangerous!', blue marker, with the words `Chosen Occupied: Avoid!', or variations of such.



The Boardwalk and surrounding area?  Green marker, `Skitter: Low threat, free supplies?'



I looked and noted that Tattletale's area was partially blocked in by black marker.  According to the map it was contested by an overlapping of Grue's territory and the Merchants.  Red pins marked some of the areas.



I supposed that made sense.  If she left her own territory empty, it would be conspicuous, and it would be strange to mark it as Tattletale's when she hadn't done anything noteworthy to claim the space.



``Where did you say your house was?'' Lisa asked the older woman.



``Dewitt and Pagne.''



Lisa turned and found the area on the map.  She held the marker so it hovered over the spot.  ``And they'd moved in?  You're sure?''



``They've been there for four days, as far as I can tell.  I'm afraid to get too close, but there's always people there.''



Lisa colored in a small section of the map with yellow highlighter, extending the size of a nearby block of the Merchant's territory.  ``I know it's small consolation, but at least now others will know to steer clear.''



``Okay,'' the woman answered with a note of sadness in her voice. ``That's all I wanted.''



``Things \emph{will} get better,'' Lisa promised, smiling gently.



The woman smiled back in return, glancing at the open area of cots and displaced people.  With a light laugh, she said, ``I suppose they have to, don't they?''



``That's the spirit.'' Lisa grinned.



She was still smiling when she turned my way.  ``Lost and found?  Want to check how your neighborhood's doing?  If you're looking for someone, you can leave a photo.  Every night, I'll be taking digital photos and sending them to the other shelters.''



I resisted the urge to roll my eyes.  ``I'm here because a \emph{friend} invited me to a party.''



She winked, then shouted, ``Dimitri!  Take over for me!''



A man from the crowd behind me shouted his response.  Lisa waved me behind the counter and led me through a door.



``Surprised you aren't running this place,'' I told her.



``Too obvious,'' she answered with a smile.  She threw one arm around my shoulders.  ``And this lets me be right at the center of things.  Information from the people who are out there every day, watching.''



``Good setup.''



``And it gets better, because I have \emph{this}.''  She opened another door.



The room was small and it was hot with the running computers that were crammed into it.  Six people were seated at different points in the room, each with their own computer.  Two more computers sat unoccupied.  The walls were scattered with photos, maps, printouts and post-its.  Black tape joined these elements together in a bizarre configuration that looked like part tree and part maze.  All of our enemies were up on the wall: The Merchants, Fenrir's Chosen, the Pure, the Protectorate, New Wave and the Wards.  There were pages relating to something Lisa was calling Case 53.  Dragon was up there, as was Scion.  The Slaughterhouse Nine were on a bulletin board, but Hatchet Face's picture was crossed out in red marker.



``Impressive.''



``I'd like to think so.  With word-of-mouth and gossip from the crowd out there and the web info and the concrete data in here, I'm pretty in touch with all that crap.  Except it's tiring.  I'm feeling the beginning of one of those headaches I get when I use my power too much.  So you and I are going out for some fresh air.''



``Knowing where we're going, I doubt the air's that fresh.''



``It's a saying, kiddo,'' she smiled.



``I know.  I'm just a little worried about there being trouble.  I\ldots'' I lowered my voice, all too aware that Lisa's computer guys could see me unmasked.  I didn't want them to connect the dots.  ``\ldots{}just feel uncomfortable without my stuff.''



``This is strict recon.''



``And the people we're doing recon on are dangerous.''



``True.  But we'll have escorts,'' she led me into another room: hers.  A quick glance around showed that a section at the back was curtained off, while the front had a desk with a computer, a bank of phones and two television screens.



``Escorts?'' I asked, as the door closed behind us.



``Like dates for a really fucked up prom.''  She worked her cell phone out of the pocket of her jeans and dialed. She held one finger up for me, telling me to wait and be silent.



It took a moment before she spoke, ``Minor?  I want you, Senegal, Jaw and Brooks in my office.  Civvies.''



As she put the phone away, she shrugged at me.  ``I know you'd rather Brian come with, but he's got his own thing going on, you know?''



``Oh, no.  I'm ok that he isn't coming,'' I told her.  ``Things are bad between us.''



``I totally didn't know you'd confessed to him, you know?  I saw the awkwardness between you two, and the distance, but I assumed it was because you'd used him as a shoulder to cry on.  My power filled in those blanks all wrong.''



``Yup.  Confessed.  Not sure what sucked more.  Him saying he thought of me in the same terms as he thought of Aisha, that he considered me a friend, knowing I'd fucked said friendship up, or him implying he'd only been nice to me because he pitied me.''



She frowned, ``I'm going to kick his ass, for being that--''



``No!''



Lisa frowned at \emph{me}.



I went on, ``Don't interfere, don't make things worse than they already are.  He's mad at me, he's hurt by what I did, and, um,'' I bit the corner of my lip between my teeth, tried to think of how to gracefully state what I wanted to say, ``We're already separated.  You get what I mean?  We're each in our own territory, doing our own things.  If something happened to push us further apart, I dunno if I'd even ever get his friendship back.''



``Oh, Taylor, no--'' Lisa started.  Before she could launch into any reassurances, there was a knock on the door.



``Come in!'' Lisa called out, then she told me, quickly, ``We'll get into this later.''



Seeing the first three men come into the room, I was left with the distinct impression that Lisa had picked out the biggest, meanest looking men in her retinue.  Then I saw the fourth guy.  Where the first three were in the neighborhood of six feet in height, physically powerful, the fourth was an inch or so shorter than I was, though he was still in good shape.  Better shape than me, for sure, but not someone imposing, like the rest.



Of the four, I noted the guy who was wearing the most wrinkled clothes, with the thick beard and the broad gut.  He wasn't imposing because he'd packed on muscle like the others, but because he was \emph{big}, looking like a grizzly bear that was dressed up like a person.  What caught my eye, though, was the ironic fact that this same guy was having the hardest time at shrugging off that stiff-backed, square-shouldered military bearing that had been hammered into him at some point during his onetime career.



These guys were soldiers.  Coil's, and now Tattletale's.



Lisa pointed at one of the taller men, a blond guy with a long face.  Not long in terms of being sad, but in terms of how genetics had put it together.  ``Minor.  Team captain.''



The next guy, darker haired, with unshaved scruff on his cheeks and chin, she identified as Senegal.



She smiled as she turned to the burly, overweight man.  ``Jaw.  I'm still waiting to hear where he got the nickname.''



``No comment,'' Jaw rumbled.



That left only the smaller guy.  ``Brooks,'' she told me, ``Our field medic, though I'm hoping we won't be needing his services there, and ex-airforce.  Handy with radios and computers.  Also pretty good with a gun.''



Jaw nodded assent to that.



``These four will be our lookouts, bodyguards and helping hands on our little errand.  We can pose as couples.''  She grinned at that.



Brooks spoke, and his voice had a hard sing-song accent I had a hard time placing, ``Couples?  Four guys and only two girls?''



``Minor escorts me.  Senegal escorts my friend.  And\ldots'' she took Jaw's hand and placed it on Brooks's shoulder.  ``You have your date.''



Jaw laughed, and Brooks turned red, anger etching his face.



``The fuck?'' Brooks growled.



``Watch it,'' Minor spoke.  He didn't raise his voice or add any inflection, but I could see Brooks react as if he'd been slapped.



``I could have brought Pritt,'' Lisa admitted, ``But I'm more comfortable with there being more guys in our group.  Chances are good we'll get in a minor scuffle somewhere along the way, and way the Merchants operate, they're going to respect guys more.  Ready to head out?''  She looked at her cell phone's display.  ``Party starts soon, and we've got to walk.''



Lisa removed the orange vest and name tag and then walked around to her desk to retrieve a series of colorful elastic bands.  She snapped one around her left wrist, then handed two to Minor.  She wore one yellow.  He wore one yellow and one black.



That done, she led the way out of the shelter, giving a sloppy salute to her `boss' at the front desk.  Together, we walked as a crowd.  We were a block away from the shelter when Senegal put one hand on my shoulder and pulled me closer.



Uncomfortable, I looked up at him to see his expression, and I didn't like what I saw.  It reminded me of a look I'd seen on Bitch's face from time to time.  That look where I could see that animal that had been at the core of any of us since before we walked upright.  Just like Bitch, the animal at Senegal's core was vicious.  The difference was that he was much better at pretending to be normal, and his animal wasn't angry.  It was \emph{hungry}.



He wore a polite smile and wasn't doing anything more offensive than holding me, but something in his demeanor told me that Senegal wasn't bothered in the slightest to be a thirty-ish guy with a teenage girl in one arm.  Just the opposite.



``Hands off,'' I told him.  I didn't want to remove his arm because I knew that if I failed, if he resisted me, it would only reinforce his position over me.



He didn't budge.  ``Your \emph{friend} there is the one calling the shots, and she said we're a couple.  Until I hear different--''



``Knock it off, Senegal,'' Lisa ordered him.



The soldier backed off, raising his hands in an `I'm innocent' gesture.  That fake smile was still plastered on his face.  Would I even know it was fake, if I hadn't spent the time around Bitch?  Or would I just think he was a slightly awkward guy with poor sense of boundaries?



Coil's guys were supposedly all ex-military.  My gut was telling me that Senegal hadn't finished his tour or whatever the terminology was.  I couldn't picture it any other way, having seen what I had.  He'd been relieved of duty.



``The rest of you walk ahead,'' Lisa instructed, ``I want a few words in private with her.''



``Who is she, anyways?'' Brooks challenged her.  ``Far as I can tell, she is dead weight.''



``I'm saying there's a reason she's here,'' Lisa spoke, her voice firm.  ``That's good enough for you.''



``But--''



``Brooks,'' Minor cut him off.  ``Come.''



Lisa and I let the others walk a bit ahead.



``Doesn't look like things are perfect here,'' I muttered.



``I might have made a move for my territory sooner, if I wasn't trying to wrangle this.''



``Why'd you stick me with Senegal?''



She frowned.  The others had gotten far enough ahead of us that she felt ok to start walking.  I joined her.



Lisa explained, ``Logistics.  I needed Minor around so I could have words with him about our long-term plans, and because I want to build a rapport.''



I nodded.  I wasn't going to argue that point.



``The problems are Senegal and Brooks.  They've become friends, and Brooks is the kind of guy that's influenced easily by his peers.  He's \emph{good}, he's useful, but he wants to be in Senegal's camp, and he's not smooth enough to pull off what Senegal does, even if he's smart enough to see what Senegal's all about, so all you get is a dick who could be dangerous if things go the wrong way.  I wanted to keep them separated, so I couldn't pair them together, and things would be \emph{worse} if I stuck you with Brooks, on a lot of levels.''



``Okay.  But you have other guys, right?''



``Pritt and Dimitri.  Dimitri's second in charge of the group, and he's the only one other than Minor who I trust to run the shelter and everything that goes on in the background.  Our stuff.  Pritt's good, she's capable, but she's a hardass in a way you see with some women in a job dominated by men.  CEOs, high-end lawyers, police officers\ldots''



``And soldiers.  Right.''



``Right.  Compensating for something.  She'd do more harm than good if I left her behind without someone else to supervise, and I already said why I didn't want her along in our group.  So long as our guys outnumber the girls, we'll look less like potential victims.''



``Okay.''



``Put up with Senegal.  Hell, if you're uncomfortable around him, use it.  Not everyone that's at the Merchant's party will be a willing participant.  We'll fit in \emph{more} if you act skeeved out by him.''



I crossed my arms over my chest and brushed at my shoulders, as if it could shake the feeling of Senegal's arm resting on me.  ``I don't like showing weakness to a person like that.''  \emph{To a bully}.



``Play along, and I'll make sure you never see him again after tonight.  We just need him for this one errand.  He's got that look that can scare people, without being too obvious about it.  Between him and Jaw, we actually kind of look like Merchants.''



``Okay,'' I spoke, jamming my hands into my pockets.



``Tell me about your territory grab?''



I did, going into detail about the play I'd made, dealing with the Merchant who had tried to cut me, encountering Battery, then returning to my lair to fend off my enemies from a safe vantage point.



``\ldots{}Problem is my range only extends eight hundred feet or so around me.  My territory's larger than that, which means I can only cover part of my territory at a time.  It bugs me, because I know I \emph{can} reach further, I've had times where I could.''



``Right.  I remember you asking about that, but I was distracted.''



``Any ideas?''



``One theory, and there's a good bit and a bad bit to it.''



``Yeah?''



``Just going by how my own power fluctuates, hearing what you're saying about yours?  You got a range boost that day of the hearing, right?  When you went to your school to talk about the bullies, and everything fell apart?''



``Right,'' I said.  ``And the day Leviathan came.  It wasn't just range.  The bugs were responding just a bit faster.  Maybe a tenth of a second faster, but yeah.''



``Ok.  Here's my theory then.  I think your power's strongest when you're closest to the situation where you had your trigger event.''



``What?''



``Honestly, I'm highly suspicious that it's true for any cape out there.  Whenever you're in the same kind of mindset or same sort of physical situation you were in when you got your powers, your powers get stronger.  The bad news is that you probably can't leverage that to your advantage.  Your powers would operate off of hopelessness and frustration, because that's what drove you to get your powers in the first place.''



\emph{Fuck}.  It fit, more or less.



``The \emph{really} scary part is that it might be doing us a disservice, because it works like a Pavlovian trigger.  Like how the dog who hears the bell ringing every time he gets food starts to drool when he hears the bell, this might be subtly urging us back into ugly, violent or dangerous situations with the benefits of having our powers temporarily boosted.''



I wasn't sure I liked the implications of that.  ``Then what's the good news?''



``It's kind of like a defense mechanism.  The worse a situation gets, the stronger you'll get.  It's probably happened before, to small degrees, but you haven't noticed it.''



``You said you saw evidence of it in your own powers?  Can I ask?''



Lisa looked back over her shoulder, as if checking nobody was following us.  She sighed.



``I don't want to press,'' I hurried to tell her.



``Another time?'' she asked.  ``I don't want to get into a bad headspace just before we do this thing, tonight.''



``That's fine,'' I answered her.  ``Really, you don't have to say.''



``I said no more secrets, didn't I?  Just give me time to figure out how to explain.''



``Of course.''



She gave me a one-armed hug.



I realized where we were going well before we got there.  Even hearing the music and knowing who the Merchants were, I was still shocked to see it.



Weymouth shopping center, the mall I'd gone to all my life, was now a rallying point for Merchants.  Hundreds of them, it looked like, all gathered together for one grand, debauched festival.



Half of the Merchants I could see wore a fresh band around their wrists, or hanging from their clothing, like badges of honor.



Lisa had noticed it too.  ``Yellow bands were for a test of courage, black for near death experience.  The red ones they're handing out at the door?''



``Blood?'' I guessed.



``Bloodshed, yeah.  Something ugly's going to happen tonight.''





