





Leviathan's attack and the waves had done a huge amount of damage to the shopping center, and it seemed like the Merchants had interrupted the efforts to shore it up and rebuild.  Construction equipment had been left behind and bore the decorations of the same hooligans that had hotwired and taken them for their own use.  The bulldozer closest to me had been spray painted in hues of purple, blue and red, and it had bras, children's toys and defaced flags strung around it, among other things.  Clothes racks from one of the clothing stores in the mall had been tied crudely to the scoop and the jutting parts had been clubbed into rough points, as if they thought they could use the vehicle to run into people and impale them.



Trash cans had been dragged into place around the mall, and burned with an acrid smell of melted plastic and rancid meat.  Countless Merchants had gathered, some perching on piles of trash or rubble as lookouts, and it seemed like everyone was striving to be heard over the music that blared from the countless speakers that were set up in and around the mall.  Not every set of speakers was playing the same music, or even the same \emph{kinds} of music.  The blend of a half-dozen techno, dance and rap tracks devolved into a single grating, uneven noise.



Senegal put his hand on my shoulder again, and I didn't stop him.  As a group, we approached the side of the building where two larger guys were standing guard. They noted the elastic bands that Lisa and Minor wore, handed each a red elastic, and then waved them through.



``They're with us,'' Lisa spoke, gesturing towards the rest of us.  The guy gave Senegal and I the go ahead to pass, and I took the offered rubber band and pulled it around my wrist.  The second we were clear, I brushed Senegal's hand from my shoulder.  He smirked at me in response.



``No faggots,'' the other man spoke.



We looked back and I saw Jaw and Brooks with a small crowd around them.



Jaw looked at Lisa, and she gave a discreet hand signal, making a fist and tapping her leg twice.



A moment later, Jaw was stepping in close and slamming the heel of his hand into the doorman's nose.  He fell roughly on a pile of rubble, and his `friend' who'd been guarding the door with him stepped forward.  Jaw caught the man's hand and pulled him in close, smashing his skull into the man's nose.  As the man fell, blood gushing from his nose, Jaw straightened, cracking his knuckles.



``Anyone else want to complain?'' Jaw asked.



Nobody did. I was surprised at how quickly people backed off and went back to whatever they'd been doing before.



Jaw collected two red elastics, put a hand on the small of Brooks' back and nudged him inside.



The interior was so crowded we could barely navigate, and it was rank with the sweet and sour smells of sweat and garbage that had just started to reek.  Body lice had found hosts with a full fifth of the people here, and more were spreading to new hosts in the shoulder to shoulder press of the crowd.  The tide of bodies around us might have crushed us if our bodyguards weren't clearing the way.  Senegal and Minor simply pushed through the crowd with enough force that some fell over, while Jaw and Brooks followed our group.  Nobody complained too loudly, and from the way others took it in stride, it seemed this was the norm.  Here, I was coming to understand, might made right.



Judging by the packs of people, `might' wasn't necessarily physical strength.  Those who had the force of numbers at their backs or the better weapons could do what they wanted.   If they didn't have numbers, sheer physical strength or weaponry that put them one step above the other guys?  They became victims instead.



``Want to buy a lady?  Or maybe a sir?'' one of the vendors leered at Minor.  A group of men and women were gathered in a `stall' behind him, watched by another Merchant.  Were they whores or slaves?  I wasn't sure I wanted to think too long about it.



``No,'' Minor answered.  ``Have a girl.''



``Get a second!  Or do you want something else?  Got bullets, got some treats.  Booze?  Bad?  K?  Decadence?  Madman?  Nose powder?''



``Not interested,'' Minor answered.



``Not.  Interested.''  The Merchant rubbed his chin, looking skeptical, ``Right.''



``Wait,'' Lisa grinned.  ``Decadence sounds good.  How much?''



``Twenty per.''



``Bullshit,'' she replied.  ``Not even if it was pure, which it probably isn't.  Eight bucks.''



``Ah, we have an expert here, do we?  Can't blame me for trying.  You have to understand, it's hard to get product with things the way they are.  Ten.''



``Eight.''



He looked around, stared at her for a few seconds, then conceded, ``Eight.''



``For me and two of my buddies here.  That's twenty-four bucks?''



The man nodded eagerly, ``Twenty-four.''



She forked over a ten and a twenty and collected her change and three pills.  She turned to me, ``Open up.  It's ecstasy.''



``I dunno,'' I answered her, feeling legitimately nervous.  I didn't want to refuse her outright and blow our cover, but I definitely didn't want to get high.  I was uncomfortable enough with the idea to begin with, but doing it here, in this kind of chaos?



``Trust me,'' she told me.



Obediently, I opened my mouth.  She pressed one small pill down on my tongue.  I closed my mouth.  She turned to Brooks and gave him one as well.



As our bodyguards led us through the crowd, she leaned over until our heads were touching, ``Sugar pills.  A little sleight of hand on my part.  Just for appearances.  Don't stress.''



``Could've fucking told me,'' I hissed.  I wasn't sure if she could hear me over the pounding music, but if anyone could fill in the blanks in what I'd said, it would be her.



More people were pushing product and stolen goods at the edges of the mall, some pimped others or prostituted themselves, while yet others were scrounging through the stores and then offering their finds for cash or barter.  The roof at the center of the mall had collapsed and what remained was shored up, but there was a gaping hole that was open to the darkening sky.  Beneath that hole, the party was already underway.  People were dancing, fighting, clustering in groups or chanting.  Sometimes two or three at a time.



As we found some breathing room, Lisa gathered the group together.  I withdrew the picture, ``We're looking for this guy.''



Nobody disagreed or debated the point, not even Brooks.  Senegal had dropped the smirk and was all business as he remained at my right shoulder, tall enough to see over the top of the gathered people.  On the far end of our group, Minor did much the same thing.  That left Lisa and I between them.  Brooks and Jaw left to go looking on their own.



In front of us, someone got tackled to the ground.  His attacker began pounding at his face, while the people around them cheered.  We detoured around that group, which brought us face to face with an exhibition.



The scene was set at the front of a woman's clothing shop, and the window had been shattered.  Where the mannequins stood in the display window, there were three women and a girl.  The women were trying on their clothes, openly undressing and then dressing in whatever the throng of people around them threw their way.  Their eyes had the glazed over looks of people who were on something, and their skin shone with a faint sheen of sweat.  They smiled as they posed provocatively and hugged the mannequins, showing off the clothes.



As if the clothes were what the crowd was there to see, and not the skin that was revealed while the women changed.



The teenage girl at the far right of the stand was another story.  She was dark-haired and the makeup she wore looked like it had been applied by someone who hadn't used makeup before.  She clutched the collar of her sweatshirt in both hands and stepped back as the crowd surged forward, reaching for her.  Being barefoot, she couldn't step down from the display platform without stepping onto broken glass, and any attempt at running would only lead her into the reaching mass of Merchants.  If she'd taken the same drugs as the other women, fear had already sobered her up.  She looked entirely alert and she looked \emph{terrified}.  No red band on her wrist.  She wasn't here by choice.



Someone climbed up onto the platform, grabbing at one of the women.  He wasn't up there for two seconds before the crowd dragged him down and threw him to the ground.  The people around him stomped and kicked him for his temerity.



That was social cooperation on a really twisted level.  From my interpretation, they weren't doing it for the women, but for themselves.  They all wanted the women, but if someone stepped up to take one for himself, they'd collectively beat him, for trying to take what they'd silently agreed to share by way of watching.



That meant the teenage girl's situation was especially grim.  She couldn't run, and if she didn't give the crowd a show, they'd lose patience with her and treat her just as they had the other guy, or worse.  If she did give them a show?  With the way emotions were running high, I expected things would turn ugly right around the moment the crowd started to get bored.  Exhibitionism would only buy her time.



``Let's go.'' Lisa pulled on my arm.



``We should help her.''



Lisa glanced at the girl, ``There's at least a hundred people here that need help.  We can't save them all.''



``We should help \emph{her},'' I growled the words, ``I won't fucking sleep tonight if I walk away from this.''



``You've got a little superhero showing through, there,'' she whispered right into my ear.



``I \emph{am} going to help her, with or without you,'' I hissed, ``Even if that means using my powers and throwing subtlety to the winds.''



``Okay, okay.  Probably don't have to go that far.  Hold on.''



Lisa pulled on Minor's arm, and he bent down so she could speak in his ear.



Minor straightened, and with one fist clenched, he made his way through the crowd, pushing people to either side, and then stepped onto the stage.



The insults hurled his way were impossible to make out over the noise of the music and the larger crowd.  He ignored them as he stepped behind the girl, caught her around the waist, and then threw her over one shoulder.  She screamed.



``I'm buying this one!'' he hollered, ``Whoever brought her, here's your fucking money!''



He revealed what was in his clenched fist – money and pills.  The sugar pills Lisa had brought?  He cast them into the crowd, and in that instant, the exhibition was over.  The crowd tore into one another, fighting over what had fallen onto their heads and shoulders, or drifted past them onto the ground.  The other women backed into the clothing store.



As Minor plowed his way through the crowd, Lisa lunged forward.  She caught the wrist of an older man, and I saw that she'd just stopped him from turning a knife on Minor.



I moved to back her up, kicking the guy in the side of the knee.  He dropped the knife and it skittered along the floor to the boundary of the crowd.  I fell on top of it, covering it with my body to prevent anyone else from taking it, then grabbed it for myself at the first opportunity.  Senegal helped clear the crowd out of the way so Minor had an exit route, and I stood, pointing the knife at anyone who looked like they might make a move for us.  The size and muscle of our bodyguards posed too much risk for the Merchants here, with the potential rewards of getting the girl from them being far too scarce compared to the immediate rewards that were in arm's reach.  The crowd let them be and continued to scrabble for the bills and pills.



We legged it in making distance from there, and the girl screamed and kicked the entire way.  People around us laughed and hooted.  I couldn't make out everything that was said, but there were lewd comments and dirty remarks cast our way.



I was swiftly losing faith in humanity.  Not that I had much to spare.



How many people had joined the Merchants after everything went to hell?  One in two hundred of the people who'd declined to evacuate the city?  One in a hundred?  One in fifty?  How many of these people had been ordinary citizens until civilization broke down?  Had I passed any of these people on the street while going about my day?



We headed into a hallway that branched off into a side entrance and bathrooms, but the rubble blocking the door and the lack of water in the bathrooms left little purpose for the area beyond being a quieter spot, away from the party.  Lisa signaled, and Senegal moved to stand guard at the entrance.



The hallway now held only Minor, Lisa, me and the rescued girl, along with two small groups of younger people.  There was a couple making out at the far end of the hallway, getting hot and heavy, oblivious to their audience.  Nearer to us, in the alcove that led to the out-of-order bathrooms, there was a trio of teenagers that were so plastered with drink that they couldn't sit upright.  Empty bottles were scattered around them.  It was as much privacy as we'd get.



Minor put the girl down, and she immediately shrank back, getting her feet under her as if ready to bolt.



``You're safe,'' Lisa assured her.  ``We're not doing anything to you.''



The girl wiped at her eye with the back of one hand, smearing thick eyeshadow and eyeliner across her temple.  ``But-''



``She's right,'' Minor spoke, standing, ``You're as safe as you're gonna get for the next little while.''



``Oh god,'' the girl sobbed.  She moved forward, ready to give Minor a hug, but he stopped her with a hand on her shoulder.  He didn't speak, but only turned to Lisa.



``Don't thank him.  Thank \emph{her}.''  Lisa looked my way.  ``We wouldn't have gone out of our way to help if she hadn't been stubborn.''



Before I had a chance to respond, the girl threw her arms around me, hugging me tight.



Lisa motioned to Minor, and he headed off to join Senegal in guard duty, leaving the rest of us alone.  Better, probably, if the girl's state left her uncomfortable or spooked around guys.



``Thank you,'' the girl sobbed into my shoulder.



I hugged her back, reflexively, a little shaken.  Why had it taken this long for someone to say that simple thing to me?  I'd wanted to be a hero, once upon a time.



``I didn't do anything,'' I managed to get the words out.



``Thank you,'' she repeated.



I stood, letting the girl rest her hands on my shoulders to get to a standing position herself.  I glanced at Senegal and Minor.  No problems there.



``Oh my god.''  I wasn't sure who it was.



It was the girl we'd rescued, staring at me.



``What?''



``You go- you went to Winslow High.''



``No,'' I stepped back, pulling my shoulders out from beneath her hands.



``Yes.  You're the locker girl.  I almost didn't recognize you without the glasses, but everyone at school knows who you are.  You're with the \emph{Merchants} now?''



``You're thinking of the wrong person,'' I said, with a note of irritation in my voice.



``No, I'm almost positive.  You were that girl that got shoved in that rank locker with all that stuff they carted away in biohazard bags.  The girl who went so mental they had to have a group of cops and paramedics haul you away for the first month of the semester.''



``Enough!'' I shouted, suprised at my own temper.  The group of teenagers who were having drinks by the bathroom turned to look at us.



Seeing my burst of anger, the girl did a complete one-eighty, from awe and surprise to desperate apologies.  That didn't necessarily improve things.  ``Oh god, I'm sorry.  You know, I didn't think about how it would bother you, saying that.  I really did want to help, you know, to do something back then, but-''



``But you didn't,'' I growled at her.  ``Just like everyone else, you left me in that locker.  You didn't go get help.  You didn't report the people who did it, not even anonymously.  You \emph{felt bad}?  You \emph{wanted} to help?  Is that supposed to mean something to me?  Is it supposed to be some consolation? You were too lazy or cowardly to step up and do anything about it, but hey, at least your heart was in the right fucking place, huh?''



``No, that's not\ldots'' there were tears in her eyes, and she was having trouble stringing words together.  I should have felt bad, for going off on someone who was probably in a pretty delicate emotional state, but I wasn't feeling particularly gentle.



``You obviously heard the story about me being hospitalized, you probably helped \emph{spread} it.''



``You don't understand,'' she said.  She startled as Brooks passed Minor and Senegal and approached us with a brisk stride.  It threw her off her stride, and she stumbled over her words as she tried to pull her excuse together.  ``Um.  It, um.  It was Emma Barnes, she-''



Brooks had reached Lisa's side and informed her, ``Found him.''



``Emma Barnes what?'' I asked the girl, trying to bring her focus back to the conversation we'd been having.



She looked from Brooks to me, and I could see how lost she was.



``Nevermind,'' I cut her off before she started stumbling over her words again.



``What's going on?''  the girl asked.



``We came here for an errand,'' Lisa answered her, ``Up to `locker girl' here to decide if you can tag along.''



``You can't- you can't leave me here,'' the girl said, eyes widening.  She looked to me, pleading.



I sighed.  ``She can come.''



``More dead weight,'' Brooks frowned.



I raised an eyebrow.  ``For someone with the primary job of giving people medical care, you're pretty dead-set against helping others.''



``I have a low tolerance for people who get themselves into an ugly situation and then expect others to bail them out.''



``That's fine,'' Lisa said.  ``Just so long as you do your job.''



``I always do,'' Brooks retorted.



``What's going on?'' the girl said, for the second time, ``Who are you?''



``Just shut up and keep up,'' I said.  We joined Senegal and Minor at the entrance to the hallway, then followed Brooks's lead as he strode across the mall.  We got bogged down once more in the press of people dancing, jumping and grinding in the center of the mall.  We would have lost sight of Brooks, but he hopped up onto the side of the water fountain by the collapsed stairwell to get high enough for us to see him.  Minor and Senegal cleared the way for the rest of us.



``I'll do the talking?'' Lisa offered.



``Sure,'' I said.  It made sense.  If we did rescue Bryce, I didn't want either him or his sister making a connection between Skitter and the girl in his rescuer's group.



As we reached the side of one grouping of stalls, I spotted Jaw standing in front of Bryce.  He had one steel-toed boot planted on the same wooden bench that Bryce was seated on, his broad gut almost in the boy's face.  Beside Bryce was a teenaged girl with bleached blond hair, who was almost lying across the bench in her attempt to keep back from Jaw.  There was nobody near enough to Bryce to be his kidnapper, nobody with a weapon, no handcuffs or chains.



Shit.  I didn't like what that suggested.



``This your boy?'' Jaw asked, as he noticed us.



``Yeah,'' Lisa said, without even glancing at me.  ``What happened, Brycie?  You join the Merchants and neglect to tell your sister, go to stay with her, and then give all the info on where she's staying to your new friends?  You that big a scumbag?''



Bryce scowled.  I could see him trying to look confident in front of his girlfriend.  ``Not what happened.''



``Then tell me a story, kid.  Keep in mind, what you say plays a big role in what happens in the next few minutes.''



``There's no story to tell,'' Bryce glared at her.  ``Our house falls down, my family moves in with my dad's friend.  Everyone else goes to work, I'm left with two of the lamest fucking families ever.  I was doing more chores in a matter of days than I've done in the rest of my life combined.''



``Poor baby,'' Jaw rumbled.  Bryce looked up at the man and then looked away, angry.



``Got sick, then when I get better my sister drags me to this church, same fucking thing.  Lame people, lame place, and I just know I'll be doing more fucking chores to `earn my keep'.  Fuck that.  Some people came to trash the church, and I figured, hey, there's a way out.  Have some fun.''  He cast a quick glance at the bleached blond girl next to him.



Fuck.



``Got a reality check for you,'' Lisa told him, stepping closer, ``Those people who `trashed' the church?  They hurt your sister.''



``What?  No-''



``She's in ICU, bro,'' Lisa lied.



I didn't get a chance to see where she was going from there, because Lisa was interrupted by a booming voice that rang through the entire mall.  ``Hey Sisterfuckers!''



The music had died all at once, and a slow roar spread through the entire mall, rising to a climax.  Cheering.



All heads were turning to look the same direction.  I followed their line of sight.



A crude platform had been pulled together at one side of the mall, where the rubble was piled highest.  The leading figures of the Merchants stood at the front, just behind a railing of metal bars that had been haphazardly welded together.



Skidmark held the microphone and wore his traditional costume, dark blue and skintight, with the lower half of his face and the area around his eyes exposed.  As costumes went, it was pretty lame, even with the cape that he'd added since the last time I'd seen him.  \emph{Especially }with the cape.  There were people who could pull off that sort of thing, like Alexandria.  Skidmark wasn't one of them.



His girlfriend was at his side, her shoulder touching his.  Squealer was streaked with oil stains, with some even in her hair.  She wore a white top and jean shorts that were each so skimpy that she was \emph{more} indecent than she'd be if she \emph{had} been naked.  She had a remote control in one hand, and her makeup was practically caked on.  Not so dissimilar from the girl we'd just rescued, in that respect.



Beside Skidmark, opposite Squealer, was Mush.  He bore a resemblance to a particular pink skinned, scrawny goblin of a creature from those fantasy movies.  His hair was so thin he might as well be hairless, his large eyes were heavy-lidded with dark circles beneath them, and his skinny limbs were contrasted by a bulging pot-belly.  All of the worst features of an old man and a malnourished child thrown together.  Except he was real; just an ugly, ill person.



Behind them stood their subordinates.  I recognized Trainwreck, but there were five more I couldn't place.  Five who, for all I knew, were new to the cape scene.



Trainwreck's presence was interesting.  Was he still with Coil?  On our side?



``That's more capes than they had a month ago,'' I spoke, leaning close to Lisa and pitching my voice low.



``They've been recruiting,'' Lisa muttered.



When Skidmark spoke, his voice carried through every speaker and set of headphones in the building.  ``You quim-jockeys up for tonight's main event!?  They don't get any better than this!''



The cheering swelled again, that ear-splitting sound you got when hundreds of people all tried to shout louder than the rest.



Skidmark raised his hands, and then swept them in a downward motion.  Twin shimmers not dissimilar to the heated air you saw above a hot road blasted towards the crowd.  Where the shimmers touched the ground, they changed the color of the flooring, creating bands of glowing ground six or seven feet wide.  After swirling for a moment, the colors settled into a gradient, stretching from violet on one side of the line to a pale blue on the other side.



The people who found themselves in the middle of the effect were dragged towards the blue side, as if they were standing on a steep slope.  The crowd roared, and began pushing people towards the effect.  Anyone who touched the purple side was caught with a greater force, dragged through to the blue side and cast towards the bulk of the crowd, sliding on the ground with enough force to stagger anyone they ran into.  The blue side seemed weaker, with anyone stepping on it finding strong resistance, as if they were trying to move against a strong headwind on oil-slick ground.  Only a handful of people made it out without being pushed back by the effects of Skidmark's power or by the crowd that ringed the area.



Skidmark repeated the process to draw what I realized was a crude square in the middle of the mall, the `blue' sides facing inward.  As he layered his power over the same area, the colors of the effect became darker, the ground below less visible and the effects on the people were all the more violent.  The blue sides had become dark blue, and instead of simply pushing against those who touched them, they \emph{threw} people back towards the center of the ring.



``You piss-licking losers know what the red armband means!'' Skidmark crowed, ``Bloodshed!  Violence!  We've got ourselves a free for all brawl!''



The noise the crowd made reached a peak it hadn't even approached before.



``Last five standing in the ring get a prize!'' a mean smile spread across his face.  Even from where I stood on the other side of the mall, I could see how bad his teeth were.  ``No rules!  I don't give a shitstained fuck if you jump in at the last second or if you use a weapon!  \emph{Anything goes}!''



People howled, hooted and jeered, but I could see some of the faces of the people trapped in the `ring'.  Most of them weren't cheering.



``Fuck me,'' Lisa whispered, ``He's trying to get people to have trigger events.  \emph{That's} how he's recruiting parahumans.''



``Our contestants don't seem to be too excited!'' Skidmark shouted.  ``Need an incentive?  Let me tell you cockgarglers what you stand to win!''



He snapped his fingers, and one of his powered subordinates, a woman with long hair covering her face, hurried forward.  She held a metal box.



Skidmark placed the case on the railing and popped it open.  He placed what looked like a metal canister on the railing, then withdrew the next.  By the time he was done, five metal cylinders were spaced out in front of him.



He picked up the center canister and began unscrewing it.  ``Before, we gave our winners the pick of the pick, the best stuff our boys and girls have been able to grab from the rich assholes with their fancy-as-fuck houses and jobs!''



Every eye in the place was on him.



``But tonight is fucking special, because we won the lottery when we found this shit!''



He withdrew a stoppered glass vial from the canister and gripped it in his right hand.  With his other hand, he held the stainless steel canister.  He thrust both hands over his head, each object clenched tight.



``Superpowers in a can!''





