





``Is he for real?'' I looked to Lisa for an answer.  ``Can they do that?''



``Don't think he's lying.''



The crowd roared, and I turned to see why, just in time to see the aftermath of the first attack.  One of the Merchants in the ring had just bludgeoned someone with a length of pipe.  Backing away, he found someone he knew, and through some unspoken agreement, they drew together, each protecting the other's back.



Others were having similar ideas.  Groups of friends were banding together, leaving others alone.  One of the loners found another guy without any friends around, shouted something I couldn't hear, and they drew together.  His new `friend' turned and struck him down from behind not two seconds later.  The traitor got his just reward when three young men and a grungy looking old man tackled him to the ground and started beating him.



At the corner nearest to us, a woman got smashed in the nose.  The spray of blood landed in the area of Skidmark's power and shot straight back into the melee.



Inspired by this sight, a man who stood outside the ring grabbed a piece of rubble and threw it down at the edge of the ring.  The chunk of concrete flew into the massed people, striking a man who was crouching and trying to avoid the worst of the fighting.



This act started a chain reaction.  The audience turned on the man who'd launched the chunk of rubble, clustering around him, punching and kicking him, and shoving him to the ground.  Others were inspired by his idea, and did much the same thing, using Skidmark's power to pelt the people in the arena.  One man helped by a kid who might have been his son upended a trash can on the glowing ground to send rotted food and other rubbish flying into the ring.  Others moved to stop them or shove anyone who got close enough onto the colored ground.  The violence was escalating and it didn't look to be slowing down anytime soon.



``We should go,'' Lisa said.  She turned to Jaw and ordered, ``Bring the boy.''



Jaw grabbed Bryce by the shirt and hauled him to his feet.  He pointed at the girl who had been sitting next to Bryce, ``And her?''



``Leave her.'' Lisa called out, raising her voice to be heard over the screams and cheering.  She said something else, but I couldn't make it out.



The crack of a gun being fired went off somewhere.  Instead of stopping the crowd, it seemed to provoke them, pushing those who hadn't been participating into action, like runners who'd been waiting for a starter's pistol.  It was as though the Merchants felt more secure with their hands around people's throats than they did trying to get away.



Skidmark gripped the railing as he hunched over it, grinning a smile with teeth that seemed to be every color but white.  His eyes were almost glittering as he watched the chaos he'd set in motion.



We moved as a group, Lisa's soldiers in a tight circle around us with Bryce, Lisa, the rescued girl and me in the center.  We made our way toward the nearest exit, but our way was barred by an unfolding brawl between two groups a good distance from the main spectacle.  Rivals?  Enemies seeing an opportunity to exact vengeance for some past event?



The girl who'd been on the bench with Bryce ran for the thick of the melee surrounding the ring.  She was shouting, almost screeching, ``Thomas!  Mom!''



Bryce struggled in an attempt to go after her, but Jaw held him firm.



I almost missed what happened next.  A woman from the group fighting in front of us ran, and a band of young men charged after her, which brought them just in front of us.



We collectively backed out of the way, but Bryce had other intentions.  The boy wrenched out of Jaw's grip and threw his shoulder into the small of Senegal's back.  The man was only barely able to keep from stumbling forward into the charging Merchants, but with his attention elsewhere, Bryce managed to slip past.



I joined Minor and Brooks in giving chase, and though Minor was bigger and stronger, I had the advantage of a slight build.  I ducked between the people and followed Bryce into the thick of the `audience'.



Bryce had reached his girlfriend, and wrapped his arms around her.  Still holding her, he turned to see us approaching.  I was in the lead, and Minor close behind me.



He looked the other way, past the glowing perimeter of Skidmark's arena, and I followed his gaze to where a middle-aged woman with bleached blond hair and a taller black man with a scar on his lips stood.



I recognized them from Sierra's description.  They were the same people who had attacked the church.



The man -Thomas?- beckoned with a wave of his arm, and Bryce and his girlfriend ran, dropping to the ground as they touched the border of the ring.



``No!'' I shouted, as the effect of Skidmark's power sent them careening into the ongoing free-for-all.  My voice was lost in the cacophony of the screaming, shouting, hollering crowd.



I stared helplessly at the unfolding scene.  The two teenagers managed to get to their feet and gather together with Thomas, the mother, and one or two others.  They were soon lost in the jumble of people that were all punching, kicking and strangling one another, spurred on by adrenaline, self-preservation, alcohol, stimulants and greed.  There was little enough room that when someone fell, they were trampled by those that were still fighting.



Minor reached me and ushered me back to the others, and we backed as far away from the fighting as we could.



The moment I saw Lisa, I asked her, ``Should I--'' I left my question unfinished.  \emph{Should I use my bugs?}



``No.  The moment an enemy makes their presence known, Skidmark might try to break this up and send the crowd after any unfamiliar faces.  Not saying they'd get \emph{us}, but they \emph{could}, and there'd be other victims too.''



``Fuck.'' I looked at the ongoing fighting.  ``We should do \emph{something.}''



``I'm open to ideas,'' she said.



``Can we- can't we run?'' the girl we'd rescued asked.



``Look, um, what's your name?'' Lisa said.



``Charlotte.''



``Charlotte, we came to get that kid.  My friend feels it's important, and she's usually got a pretty damn good reason for doing what she does.''



``Thank you,'' I said.



``So it's up to her, what we do here''



What were our options.  Using Lisa's power?  I wasn't sure how it applied here.  If she had a way of addressing the audience, maybe there was something she could say to turn the tide, or turn them against their leaders\ldots but the only way to do that would be to get the microphone Skidmark had.



We had Lisa's soldiers, but no matter how well-trained they were, there was a certain point where fighters in \emph{quantity} overcame fewer fighters of higher \emph{quality} in a brawl.  Not to mention that some of the Merchants had guns.  The great equalizer.  I was pretty sure Lisa's soldiers would be packing, but the problem with guns was that they drew attention, and we definitely did not want to fall under too much scrutiny.



This was what the Merchants were.  Even less organized than the ABB, they were humans reduced to pack behavior, with Skidmark and his people acting like kids who would put animals in a cage and shake it set them on each other, instead of house-training them.  None of this made the Merchants any less dangerous, though.  Just the opposite.



I had no options here, in the face of this.  The most I could do would be to use my power on the entire crowd, and that would turn this already disturbed situation into something else entirely.



``We hold our ground,'' I told Lisa, ``Unless things get bad enough that we're at risk.  We wait for the fight to end, we see if we can find him, and we make our exit.  Sticking around also means we can get more info on what Skidmark's got in those vials and where he got them.''



``Okay,'' Lisa confirmed.  ``That works.''



The minutes that followed were among the longest I'd experienced in my life.  It wasn't a tedious, slow, agonizing passage of time like I'd experienced in the hospital bed, waiting to find out if I was being arrested or if my back was broken.  No, these minutes stretched on because there was so much going on, and I couldn't lose my focus, look away or pause for contemplation for a second.



Different groups tried to pick fights with us.  It was nonsensical, given that we weren't even in the ring, but adrenaline was running high and we stood out because we were apart from the rest of the fighting, isolated.  We had stuff they could take, and warm bodies they could\ldots well, warm bodies.  It was enough.



We tried to hold a formation, with the bodyguards holding the outer perimeter and the less experienced combatants, myself included, in the center.  It quickly became apparent that these things didn't really hold up in a real combat situation.



For one thing, our enemies quickly figured out what we were trying to do and tried to force Lisa's soldiers to break ranks.  They would hang back and throw things, or stay just out of reach as they held weapons at the ready, looking for a moment when our front-line fighters were distracted or otherwise occupied.  It forced Lisa's soldiers to move out of formation to deliver with the enemy with a few decisive hits, then back up to close the gap in the line.



That was the plan, anyways, but sometimes the opponent was too nimble to be taken down, and other times, they delayed Lisa's people enough that someone could slip through the line and attack one of our less capable combatants, myself included.



I held a knife in each hand – my combat knife and the one I'd taken when we'd rescued Charlotte.  When I was forced to fight, I avoided lethal strikes.  I had a sense of where the major arteries were and avoided them, even when I knew I could make a quick cut at someone's wrists or neck.  Holding back didn't do me any favors, and I got smashed in the left ear once, struck in the gut and chest a few times, and a nail that was stuck through someone's makeshift club sliced the back of my upper arm.



Still, Lisa's soldiers afforded me time to breathe.  I remained vigilant for any break in ranks and incoming attacks.



My arm smarted where I'd been cut, and my ear throbbed.  I swallowed hard, glancing towards the ring, where people lay in heaps, and only two-thirds of the combatants were either injured, unconscious, dead or playing dead.



Feeling pressured, Senegal reached for his gun, but was forced to duck back and to the side to avoid being bludgeoned by a heavy metal lock one of the Merchants had clipped to the end of a length of chain.  The follow-up swing knocked his weapon from his hand.  Someone else, a stocky man with eyebrows like caterpillars, moved through the gap to charge for me bare handed.



Could be worse.  I set my balance and readied to strike with my knives, waiting until he closed in and-



And I was somewhere else.  It was like remembering something profound that I'd forgotten.  I'd seen this before.



Huge creatures filled my perception.



It was hard to say how I knew they were two different creatures, when each of them existed in multiple parallel spaces all at once.  Countless mirror moved in sync with one another, each occupying the same space, just as solid as the others, differing in how they moved and the worlds they interacted with.  Each of them folded, unfolded, expanded and shifted without taking more or less space.  I couldn't wrap my head around it, even as I felt there was something like a pattern there.



Some distant part of me realized I'd seen something similar to that folding and unfolding once, in a much simpler form.  A tesseract, a fourth dimensional analogue to the cube.  The difference was that while the cube had six flat faces, each `side' of the tesseract had six cubes, each connected to the others another at each corner.  To perceptions attuned to three dimensions, it seemed to constantly shift, each side folding or reshaping so that they could all simultaneously be perfect cubes, and each `side' was simultaneously the center cube from which all the others extended outward.



The primary difference between these things and the tesseract was that these beings I was looking at were alive, and they weren't simple models I was viewing on a computer screen.  They were living entities, lifeforms.  There wasn't anything I could relate to any biology I knew or understood, nothing even remotely recognizable, but they were undoubtedly alive.  They were enigmas of organs that were also limbs and also the exteriors of the creatures, each simultaneously some aspect of the entity as it flowed through empty space.  It didn't help that the things were the size of small planets, and the scope of my perceptions was so small.  It helped even less that parts of them seemed to move in and out of the other dimensions or realities where the mirror images were.



The pair moved in sync, spiraling around one another in what I realized was a double helix.  Each revolution brought them further and further apart.  Innumerable motes drifted from their bodies as they moved, leaving thick trails of shed tissues or energies painting the void of empty space in the wake of their spiraling dance, as though they were made of a vast quantity of sand and they were flying against a gale force headwind.



When they were too far away to see one another, they communicated, and each message was enormous and violent in scope, expressed with the energy of a star going supernova.  One `word', one idea, for each message.



Destination.  Agreement.  Trajectory.  Agreement.



They would meet again at the same place.  At a set time, they would cease to expand their revolution and contract once again, until they drew together to arrive at their meeting place.



-the Merchant caught me off guard, as I reeled from the image of what I'd just seen.  He caught me across the cheekbone with his elbow, and pain shot through my entire skull, bringing me halfway back to reality.  Someone grabbed me, her chest soft against my back, her grip around my shoulders painfully tight.  Charlotte?  Or Lisa?



The shift from what I had seen to relative normalcy was so drastic that I could barely grasp what I was sensing.  I opened my mouth to say something and then closed it.  I couldn't unfocus or take in the scene as a whole, as the entirety of my attention was geared for seeing\ldots what had I been looking at?  It escaped me as I tried to remember.  I shook my head, striving and failing to see past the countless minute details or the shape of things: the way the Merchant's facial features seemed to spread out as he advanced towards me, the contraction of his body as he bent down, the nicks and brown of rust on the knife he picked up, the one I'd dropped.  I still held my good knife.



I closed my eyes, trying to blink and fix the distorted focus, and it only helped a little.  I looked to my left for help, saw Minor and Jaw with their hands full, their movements too hard for my eyes to follow.  To my right?  Lisa was slumped over, and Brooks held her.  Merchants were closing in on them.  Senegal stood in front of me, and though his gun was gone, he was using the length of chain that he'd taken from one of the Merchants to drive our opponents back and buy us breathing room.  It wasn't enough.  Three capable fighters weren't able to protect seven people in total.



I used my power, and wrenched my eyes closed.  It helped more than anything, as the tactility of my swarm sense gave me a concrete, solid sense of the things around us.  Many of the Merchants had lice on their skin, in their clothes and on their hair.  A small handful of flies buzzed around the area.  With a bit of direction to guide those flies to where I needed them, I had a solid sense of my surroundings and what the enemy combatants were doing.



With panic and disorientation nearly overwhelming me, I had to resist the urge to use my power to call a swarm together.  Using this many bugs, to get a sense of what was going on?  It wouldn't attract undue attention.  I let bugs gather on the ceiling of the mall, drawing them down through the large crack where part of the roof had caved in, as a just-in-case.



I kept my eyes closed as I fought back, pulling out of Charlotte's grip to strike at the Merchant, cutting him across the forehead.  He growled something I couldn't make out and charged me.  Knowing I wouldn't be able to beat him in any contest of strength, I threw myself to one side, landing hard on the ground and nearly tripping Senegal.  I brought my knees to my chest, and then I kicked outward to strike him in the calf with both heels.



I wasn't thinking straight.  I should have predicted that he'd fall on top of me.  His shoulder hit my chest, his body weight heavy on top of me.  His knife hand was trapped under his body, near my waist.  I was more fortunate, with my right arm free, and I pulled the knife's point across his ribs, aiming for a shallow cut that hurt more than it injured.  He screamed and dropped his weapon, and I scrabbled to slide it back towards Charlotte, Brooks and Lisa.



Senegal turned and kicked my attacker away from me.  While Senegal used the lock on the end of the length of chain to strike the man in the jaw, I tried to stand.



Stupidly, I'd opened my eyes as I stood, instead of trusting to my power to keep a sense of the immediate situation.  Motion sickness hit me like a sack of bricks, and I nearly fell over.  Charlotte caught me to keep me from tipping over, only narrowly avoiding stabbing herself on my good knife.



``Oh my god,'' she murmured.  ``You're\ldots''



Had I given myself away?  I hadn't used that many bugs.



No, it was something else.  I could tell from the flies I'd placed on her head that she was looking up.  Her attention turned to me, then Lisa, and then back to the higher object.  I forced my eyes open, controlling my movement and my breathing to reduce the threat of nausea, and saw she was looking at Skidmark's platform.



Skidmark was slumped against the railing, struggling to his feet.  Squealer, Mush, Trainwreck and their other subordinates weren't faring much better.



Skidmark grabbed his microphone and broke into laughter, the nasty chuckles echoing through the area.



``Seems like one of you\emph{ assdrips} just earned his stripes,'' he cackled.



I saw a flash of white from within the ring and it dawned on me what had just happened.



Another flash sparked in the ring, then a second.  Both were in close proximity to a boy no older than I was.  White smoke poured from his eyes, nose, ears and mouth, with smaller traces flowing from his scalp, stirring his hair.



He flinched as someone whirled on him and raised their weapon, and a burst of white light appeared two feet to the other person's left.  A miss.  The person swayed toward where the flash had been, as if it had pulled at him.  The glowing boy stuck one arm out, towards his target, and another flash of white appeared a yard behind his target.



The man charged, and the boy tried a third time.  The blast intersected the man, and when it faded, the man's upper arm, forearm, elbow, and the right side of his torso and hip were gone.  Blood gushed from the area where his flesh had been carved away by the light, and his dismembered hand dropped to his feet.



The boy screamed in some combination of horror, pain and rage, and flashes of the whiteness erupted randomly around him.  Some caught people who were lying prone on the ground, others hit standing combatants, while most simply hit thin air.



A trigger event.  I'd just seen someone have their trigger event.



But what had happened to Skidmark's group, Tattletale and I?  I could vaguely remember something, thought about trying to put it into words, as if describing it could help call it to mind in a way that I could describe it, but they disappeared as I reached for them.  I was reminded of Imp's power.  Before I could get a handle on it, I'd forgotten entirely, and I was struggling to even remember what I was trying to do, my thoughts muddling the idea of it with my attempts to get my bearings.



And Charlotte, who was helping me stay balanced on my feet, was staring at me wide-eyed.  I remembered her exclamation of surprise.



If everyone on stage with powers had been affected, and Lisa and I were reacting the same way, it couldn't be that hard for her to put the pieces together.  Charlotte \emph{knew}.



I looked to Lisa, for advice or ideas, but she was still slumped over, and she wasn't recovering.  Why?  If this was some kind of psychic backlash from someone else having their trigger event, had she maybe been hit harder because of her power?



I hurried to her side, while Brooks turned to rejoin the fight and help re-establish our front lines.



``Lisa!'' I shook her.  She looked at me, her eyes unfocused.



``They're like viruses,'' she said.  Her voice was thin, as if she were talking to herself.  ``And babies.  And gods.  All at the same time.''



``You're not making any sense, Lisa.  Come on, get it together.  Things are pretty ugly right now.''



``Almost there.  It's like it's at the tip of my tongue, but it's my brain, not my tongue,'' her voice was thin, barely audible, as though she was talking to herself and not to me.  ``Still fillin' in the blanks.''



I slapped her lightly across the face, ``Lisa!  Need you to come back to reality, not go further into your delirium.''



The slap seemed to do it.  She shook her head, like a dog trying to shake off water.  ``Taylor?''



``Come on,'' I helped her to her feet.  She almost lost her balance, but she was still recuperating faster than I had.



Charlotte took over the job of ensuring Lisa was okay, and I moved forward to help back up the other guys.  With a knife in each hand, I stood behind the trio of Brooks, Senegal and Minor, ready to stop anyone who tried to slip by.  I kept my eyes closed.  I could manage so long as I didn't try to move and keep my eyes open at the same time.  It was swiftly receding.



The last group to tackle us had largely been beaten back.  Another group made some threatening moves, but they seemed to be in rougher shape than us.  Their leader was an amazon of a woman with a wild look in her eyes and matted hair, and I could see concern flash across her face as she looked us over and noted the disparity in the condition of our groups.  It struck me she was in a bad spot, knowing her group would be thrashed if she took us on, but at the same time, she couldn't order her guys to back off without looking like a coward.



Whatever decision she would have made, we didn't get to find out.



``Stop!'' Skidmark hollered into his microphone.



It took a full minute for everyone to break off in the fighting and back off to a point where they didn't feel immediately threatened.



So many injured.  How many of his own people had Skidmark just lost in this stunt?



Did he care?  He stood to gain five new parahumans for his group.  Six if you counted the guy who'd had his trigger event.



``If we wait any longer, there's only going to be one of you cockbiters left in the ring!  We got five of you fuckers left, and that's all we need!''



Only five?  There had been at least eighty in the ring at the beginning, and still more had joined the fight afterward, one way or another.



I could see the remaining five as the audience moved back to give them space.  A family of three, it seemed, a woman with a gaping wound in her stomach, her hand crimson where it pressed against the injury, and the boy who'd had his trigger event.  I didn't see Bryce or his new `family' in the mist of the people retreating from the scene.



A flash of light marked another uncontrolled use of the new cape's power.  It struck close to the ground, removing the leg of someone who lay unconscious or dead on the ground, but it left the ground perfectly intact.  Why?  When it consumed clothing and flesh but not the building itself?



``Boy,'' Skidmark pointed, ``Approach the stage!''



The ring flashed and disappeared.  The boy turned, as though in a daze.  He flinched as another burst of light sparked a good ten feet away.  He limped toward Skidmark and stared up at the Merchant's leader.



``You're gonna need a name, kid, if you're going to join the Merchant's upper circle.''



The boy blinked, looking around, as if he didn't quite understand.  Was he in shock?



``Come on, now.  Let's hurry it up.''



There was a spark of the boy's power, and the flash removed a beachball-sized section of rubble beneath Skidmark's `stage'.  The boy stared at it.



``E-Eraser?'' he answered, making it a question.



``Like the puny pink nipple on the end of a pencil?  Fuck that,'' Skidmark snarled.



``Um,'' the boy drew out the noise, all too aware of his audience, probably unable to think straight.



``Scrub!'' Skidmark shouted, and the crowd roared.



How in the hell was\emph{ Scrub }better than Eraser?  In what insane reality?



Skidmark waited until the noise of the crowd had died down before he raised the vial, ``No point in you having a drink of this shit.  Wouldn't do sweet fuck all.  Pick someone.''



The boy stared at Skidmark, processing the words.  He flinched as another flash occurred near him.  A hand clutching one elbow, he turned toward the crowd.  When he spoke, his voice was shaky, ``R-Rick!  Doug!''



Two people emerged from the massed people who stood around where the audience had been.  One had blood running from his scalp to cover half his face, while the other was coughing violently, blood thick around his mouth and nose.



``Can\ldots  Can I give it to both?  Can they share it?'' the boy with the glowing hair asked.



Skidmark chuckled, and it was a nasty sound with very little humor to it.  ``No, no.  You definitely don't want to do that.  Pick \emph{one}.''



``Doug.  Doug can have it.''



The boy who was coughing looked up, surprised.  The one with blood on his face, Rick, suddenly looked angry.  ``What the fuck!?''



A flash of white high above and to the right of the boy with the powers made everyone nearby cringe.  It tore away a chunk of a metal beam that was helping to support the damaged roof.  People were giving a wider berth to the boy with the powers.  I suspected his abilities and his apparent lack of control were the only things keeping Rick from running up and punching him.



Was this division & the hard feelings on purpose?  If it was intentional, if Skidmark was dividing his allies from their former groups and cliques so they couldn't gang up against him, I'd have to adjust my estimation of him.  Not that I'd like him any more, or even respect him, but I'd give him credit for intelligence.



``You didn't help me when I got pulled into the ring,'' the boy with the powers told Rick, ``Doug at least tried.  He gets my prize.''



As Doug approached the stage, taking the long way to keep his distance from his newly empowered `friend', I became aware that my bugs were dying on the roof, where I'd gathered a swarm in preparation during the chaos.  A patch here, a patch there.



No.  Not dying.  They were stunned, their senses obliterated by bursts of chaos and false sensations.  I had an idea of what it was.  I'd felt the same thing before.



I turned to Lisa.  Moving my left hand from the scratch on the back of my upper arm, I discreetly pointed up and murmured, ``There's company on the way.  We should go before there's trouble.''



She looked up, then nodded assent.  Tapping Minor on the shoulder, she gave him a hand signal, and he notified the others.  We began moving.



The person on the roof was joined by others.  Some bugs died beneath their footfalls.  More bugs were stunned as the first individual crawled forward on all fours, around the lip of the roof and onto the ceiling of the mall, hanging off of it by his hands.  With the building largely unlit, I couldn't make him out.



Newter was here, and the rest of Faultline's crew.



We reached the first exit, and no sooner had we reached for the door than the handle disappeared.  The gaps separating the door from the wall filled in, as though wax matching the color of the door was dripping through the gaps.  There were similar things happening at the other entrances, I saw, the doors fading into the walls, becoming little more than discolored blotches.  Nobody else had seemed to notice, with their attention wholly focused on the woman who was making her way down from the stage with the vial for `Doug'.



When the fighting had started, Lisa had dissuaded me from using my power, out of a concern that the ensuing riot and chaos would get people hurt, and that the mob might start to hunt for strangers in their ranks.



I had no idea why they were here, but it seemed Faultline was about to crash the party in a far more direct way than we had.  We were about to see that bad scenario unfold, and our escape routes had vanished.





