





Newter dropped from the ceiling.  The main part of the mall had only the one level to it, but the roof was arched slightly, and he was dropping from one of the higher points.  I was bad at estimating distances, but what was that?  Fifty feet? Sixty?



He landed in a crouch, a hair behind the girl who was carrying the vial down the pile of rubble to the base of the platform.  As she turned, dust, papers, cigarette butts and fragments of rock stirred around her.  They moved in a counterclockwise orbit, rising, increasing in intensity over a span of one and a half seconds.  Whatever her power did, Newter stopped it, smacking her in the forehead with his palm, almost gently.  She stepped back, as if she'd lost her balance.  The building whirlwind around her dissipated into a billowing cloud of dust and her legs turned to rubber beneath her as she tried to step back once more. She fell.



Newter's tail encircled the vial before she could drop it, and he flicked it into his left hand.  An instant later, he was racing for the stage, almost casually finding stepping stones as he made a beeline for Skidmark and the rest of the group.  He was going for the case and the vials.



Much of the crowd was running after Newter, rushing for the base of the stage and climbing the heaps of rubble to follow.  In doing so, they were vacating the center of the mall where the casualties lay.  I hated to get closer to the chaos, but I suspected it would be a long time before I had a better chance to find and retrieve Bryce.



``I'm going after the kid,'' I said.



``Minor, Brooks, escort her,'' Lisa ordered.



On the other side of the mall, Newter had reached Skidmark and pounced for him.  In reaction, Skidmark used his power to coat his cape in a layer of his power.  He raised it between himself and Newter.  Newter was already airborne, unable to change course, but he had the presence of mind to hock a loogie into Squealer's face.  He bounced off of the cape, knocking Skidmark back, and fell to the ground.



Skidmark used his power to saturate Newter and the ground around him.  As his power took hold, Newter was launched through the rungs of the metal railing and down into the midst of the crowd at the base of the stage.  Skidmark shouted something, but I couldn't make it out over the noise of the other Merchants.



I tore my eyes from the scene and we hurried toward the heaps of unconscious, bloodied and wounded that lay where the arena had been.  We were halfway there when the entire mall began to brighten.  The barred windows were expanding, and massive torches were lighting on the far sides.  Shafts of orange light extended into the mall's interior, patterned into diamonds by the meshes of bars Labyrinth had erected.



The wall behind Skidmark and the other `upper circle' members of the Merchants began to bulge inward.  Features took form: a face, ten feet tall.  Protrusions below it, near the floor of the platform, marked emerging fingertips.



Labyrinth wasn't stopping there.  Minor had to catch my arm and pull me back to keep me from being caught in the path of another effect in the mall's floor.  The ground cracked and bulged upward as though a mole was tunneling at high speeds just beneath the tile.



``Get back!'' someone shouted behind me.  I recognized Lisa's voice and took her advice, backing away from the hump.  Minor stopped me from backing up into another hump that had appeared behind me.



Stone walls heaved upward from the mounds of broken tile, blocking my path and stopping at a height of twelve or more feet.  As more walls rose around me, I saw a door form to my right, and the corridor to my left had a bend in it.



A maze.  She was living up to her name.



The walls at the outside edges of the mall were altering, now, more faces and body parts making themselves apparent.  Like statuary or reliefs.  Limbs intertwined and nude figures decorated the interior walls of the mall, each tall enough to extend from floor to ceiling, animated so that they moved with a glacial slowness.  With a surprising speed, the interior of the mall was coming to resemble some kind of temple.



I had to admit, I was spooked.  That girl's power was intimidating when she wasn't on my side.  She wasn't all there, mentally, so the only thing holding her back was the person telling her what to do.  If she could make those giant torches, she could set the floor on fire.  Or she could have created spikes instead of walls, without leaving the rest of us any place to run.  That nobody had been hurt was purely by her choice.



Stone poles speared down from the roof.  Looking up, I saw that the edges of the crack in the roof had fanged teeth, and that figures were sliding down the metal poles.  Two female, one obese male.  Spitfire, Faultline and Gregor the Snail?



Not quite.  Faultline and Gregor, yes.  I didn't recognize the other woman, and she was too tall to be Spitfire with her mask off.  Red haired, slender, older than Spitfire or Labyrinth had been.



She slid down the pole, up until the moment Trainwreck leaped from the stage and caught the base of the pole with his shoulder.  He was built like a football player in a quadruple-thick layer of cast iron protective gear, steam billowing behind him as he tore past the stone pole like it was nothing.  It cracked in four places, and the girl dropped out of the air.



One section of the pole hit the ground in an upright position, and she landed atop it with one foot, wobbling briefly.  Controlling the angle the pole fell, she angled her fall toward a nearby wall of the maze.



It wasn't enough.  Trainwreck smashed the pole from under her, sending her flying through the air to land in the midst of Labyrinth's maze.



Labyrinth created a short pillar below the metal case and canisters, and began to extend it towards the gap in the roof.  Skidmark used his power to force the things off the top of the pillar and onto the platform, where they rolled.  A few stray papers fluttered from the case.



There was a crack of gunfire, and I saw the momentary light of the shot to my right.  I couldn't see over the wall, but I saw Trainwreck lumbering forward, one oversized metal gauntlet raised to protect his head, the only vulnerable part of his body.  I directed some bugs to the scene, and realized that a woman with the exact same proportions as the red-haired woman was firing at Trainwreck.  She'd made it through the maze and back to the skirmish with Trainwreck so quickly?



There was a brief pause in the gunfire, then a single shot fired.  Sparks marked the ricochet between his shoulder, the back of his hand, and the armor that rose behind his head.  He dropped to one knee with a suddenness that suggested he was wounded.



I hurried to the wall.  I could use my bugs to find my way through the maze, getting a sense of the layout, but I needed something faster.  Labyrinth was using her power and adjusting the battlefield with every passing second.  The way things were, given how she wasn't aware of who I was, I was included among her enemies.  If I didn't go now and the battle resolved one way or the other, I might lose my window of opportunity to get Bryce.



There was no way I was going back without him.  The intensity of the emotion I was feeling on the subject surprised me.



I \emph{hated} the idea of going back to Sierra and telling her I'd failed.  Hated the idea of that conversation on top of the news I had about Bryce joining the same Merchants that assaulted her friend with a broken bottle.  I couldn't do it.  I couldn't be leader of a territory and know that someone out there was maybe telling others I hadn't followed through, fighting that constant nagging doubt in the back of my mind that wondered if `my' people were whispering or laughing at me behind my back.



And maybe a small part of it was that my meeting with my father had been a reminder of how important family was.  Bryce was the errant youth, his sister the anxious family member.  Were my emotions here tied to the parallel between them and my father and me?



``Help me over,'' I ordered Minor.  There was a crash not too far away as Trainwreck tore through one of Labyrinth's walls.



``Can give you and Brooks a boost, but not sure if I can follow,'' Minor told me, ``Maybe if I find a place with something to stand on-''



``That's fine.  Look,''  I drew an arrow on the wall with my bugs, ``I can give you directions.''



There was little surprise on his face at the demonstration of my power.  He gave me a curt nod, dropped to one knee, and wove his fingers together to give me a stirrup for my foot.  I sheathed my good knife, stuffed the spare between the sheath and the strap that attached it to my midsection and stepped inside the bridge of Minor's hands.  He heaved me up, almost throwing me.



The cut on the back of my arm burned as I found a grip, then hurt twice as much as I hauled myself onto the top of the wall, my toes scrabbling on the untextured surface for traction.  I reached down for Brooks, but he shook his head and waved me aside.  He wanted to come up on his own.



Fine, whatever.



I hopped down into the next corridor.  The far left had an archway leading into one of the more open areas, a circular area that was serving as a clearing for Trainwreck and the red-haired girl to fight.



I crouched down as I reached the doorway, peeking out and trusting my bugs to give me the fuller story of what was going on.  Brooks appeared behind me and crouched, gun raised, his back to the wall.  His breathing was quiet and controlled even after his recent climb and jog.



Trainwreck and the new girl on Faultline's team were facing off on the far side of this area.  Behind Trainwreck, I saw a section of wall toppling, spotted Faultline dashing through the obstruction as though it were barely there.  She ran up behind Trainwreck and slashed her fingertips across his heel as he was stepping forward.



As he set the foot down on the marble floor, his ankle shattered and his foot broke free of his calf.



He caught the ground with the stump of his mechanical leg, and she darted in close to cut through the knee of his other leg.  He fell onto his back as she slipped between his legs, and she quickly turned to begin using her fingertips to cut down the wall, like a jungle explorer using a machete to hack through brush and vines.  The red-haired woman joined her.



The ground rumbled as sections of the black marble floor rose to form into broad, shallow stairs, leading from the two young women to Skidmark's stage.  The capes in Skidmark's group were struggling to find ground to stand on, as they were crowded back to the edges of the platform by the statue that was still emerging from the wall.  A head and two forearms with reaching hands, all in dark stone.



It was eerie, to see the changes that had occurred in our surroundings in the time it had taken me to cross the wall and wait for the fight to pass.  If the attentions of the Merchants had erased any familiarity I had towards the Weymouth shopping center, Labyrinth had cremated the remains and erected something else in its place.  It was a cathedral, dedicated to a goddess that was very real and having a very active hand in current affairs.  Labyrinth.



Which reminded me of the fact that I needed to get through this maze.  Labyrinth's power was drawing many of the crawling bugs down into the ground as it refurbished the floors and consumed the piles of trash or rubble.  I still had the bugs on the ceiling, but I didn't want to give our presence away.  Of the relatively few bugs I was willing to use, a share were being used to direct Minor and placing them in strategic locations to get a sense of the layout.  As the maze took shape in my head, I showed Minor the way.



I stepped into the clearing and, double checking nobody was in earshot, I approached Trainwreck.  Brooks followed just behind me, watching my back.



Trainwreck didn't look like much, just going by the face.  He had a round face, small eyes, greasy hair tied back in a ponytail and scarred cheeks.  He looked like a homeless guy who hadn't had a shower in a long time.  The only thing setting him apart from the Merchants were the gunshot wound near the corner of his jaw and the steam-powered armor that rendered him strong enough to pound the crap out of Armsmaster.



I asked him in a low voice, ``Trainwreck.  Are you still working for Coil, or did you leave?''



He tensed, and his eyes turned my way, though he couldn't turn his head with the hardware around it.  I stepped back as he used one arm to prop himself up and get a better look at me.



``No idea what you're saying,'' he said.  He gave me a level stare, and I was almost convinced.  But I'd seen him in the parking garage when I first found out Coil was the Undersider's employer.



``Right, total nonsense, sorry,'' I said.  I tried not to show fear as he tried to get to a standing position with his ruined mechanical legs, looming over me.  ``But if you were working for the man, maybe you could find some excuse to knock over that wall over there\ldots''



I pointed at the nearest section of wall.



``You're fucking nuts,'' he told me.  He raised his arm, and my legs tensed, ready to leap towards him if he took a swing at us.  As big as he was, without him being able to use his legs, being in close would be safer than trying to leap back out of his reach.



He brought his hand down on the wall I'd pointed at to heave himself to an upright position.  The wall fell as he rested his weight on it.  Using his other hand to help balance himself, he gripped the wall in his heavy gauntlet and flung the section of wall at Faultline and the red-haired girl.  The girl turned and stepped out of the way as the wall rotated in the air, bounced between her and Faultline with mere inches gap between them, and slid back down the stairs.  He didn't pay any further attention to us as we ran for the gap he'd opened.



My power let me get a general map of the people who were still unconscious or prone, and the bugs wouldn't stand out too much as they checked the bodies.  I went by body types, trying to find people of Bryce's height and build.  The path Trainwreck had opened gave us avenues to two people who could have fit the mark, with a third over the next wall.



Good news?  The first of the prone bodies I went to was Bryce.



Bad news?  He was injured.



Scrub's power had torn through the clusters of Merchants during the fighting, and Bryce's new `family' was no exception.  The girlfriend was dead, her head and shoulders gone, muscle and fluids flowing out where the flesh had been annihilated.  The girl's mother was a goner too.  She lay on her back, her face missing.  Had she been behind her daughter, holding her, hit by the same blast?



`Thomas' was still alive, the black man with the scar on his lips.  The man who had hurt Sierra's friend from the church, who had literally torn the guy a new asshole, if I'd gotten Sierra's meaning right.  Thomas crawled slowly for the nearest arch, breathing hard, his face drawn with pain.  A slice had been taken out of his arm, shoulder, and a section of his back, as though a guillotine had grazed him from behind.  I wasn't quite sure how he hadn't died yet, with the amount he was bleeding.



Brooks stooped down to help Bryce, who had gotten off lightly compared to the others.  He was missing a large portion of his right hand, and he'd had the presence of mind to try to loop his belt around the injury to control the blood loss, pulling it tight.  He seemed like he'd lose consciousness any second.  Brooks retrieved some medical supplies from his backpack and began tending to the boy.



I watched Thomas struggle towards the door.



Minor arrived fifteen or twenty seconds after Brooks had started to work on the boy, standing guard while our medic took care of Bryce's hand.



Brooks helped Minor to get the boy to a standing position, while I watched Thomas struggle on.  He was getting weaker, fast.  The blood loss had been too severe.



Skidmark had several parahumans working for him, and I didn't know all their powers.  Maybe Thomas would get care.  Maybe Skidmark would attend to his people.



Probably not.  I knew that by leaving him here, I might be leaving him here to die, but the chance of him surviving anyways was pretty slim. Besides, bringing him would slow us down, and I wasn't sure we could afford that.



I shook my head a little, as if it could cast away the layers of little justifications and excuses I was putting together.  I was searching for a rationale, a reason to leave him behind.  Also, maybe, I suspected I was trying to give a reason to the fact that I had almost no sympathy for the man.



If I was going to leave him there, I'd own up to what I was doing.



Sierra had wanted Thomas and his followers to suffer, and I'd agreed to make it happen.  I couldn't do anything about Bryce's girlfriend or her mom.  They were dead, and it had probably been instantaneous and painless.  Thomas, though?



Brooks followed my gaze to Thomas.  In his accented voice, he asked me, ``You want me to bandage him up?  Don't know how much I can do.''



Thomas heard and stopped crawling, dropping onto his belly.  He didn't look toward me, but I knew he was listening.



``It's fine,'' I told Brooks.  ``Focus on the boy.''



He nodded, then helped hold Bryce's prone form while Minor got a better grip.  Thomas didn't move, react or say anything.



``Let's go,'' I said.



We ran, and with Brooks keeping one hand on my shoulder to guide me, I glanced behind us to get a sense of what was going on.



The battle was still ongoing.  Gregor the Snail was here, but unlike the others, he wasn't operating in Labyrinth's world.  He passed through the walls of the maze, spraying streams of slime at Trainwreck, who had apparently advanced halfway up the stairs by using his hands to help him walk.  Trainwreck retaliated by throwing a chunk of stairs at Gregor with one hand while trying to block the stream of slime with the other.  The section of stairs hit the wall of the maze just in front of Gregor, some of it bouncing over to pass through Gregor.  Not real, as far as he was concerned.



What did this look like to Gregor?  Was he standing in the mall as it had been, while Trainwreck seemed to stand on thin air?  Or was Trainwreck on the ground?  I couldn't parse it.



Mush had started pulling himself together, but Labyrinth was making his job into a struggle.  His right arm had divided, stretched, forked out and reconfigured until it looked like a mass of reaching veins and arteries.  He plunged it into one of the trash cans that Labyrinth was absorbing into the floor, and when he withdrew it, the tendrils had formed the connective tissue for an oversized hand crafted out of garbage.  His other arm and much of his lower body had already gathered some garbage around it, letting him stand several feet taller than he had before.  The skin of his head and body was peeling off into more tendrils, reaching for more trash and distributing some from his arms to his torso.



From what I could gather, he needed some kind of loose matter to form the body of his other self.  Dirt, compost, trash, maybe even sand.  Problem was, however fantastic his surroundings might have been for this five minutes ago, Labyrinth was screwing him over by cleaning things up, maybe inadvertently.  One upper arm, his naked upper body and his nearly bald head were all exposed and vulnerable.



Scrub had climbed up to one corner of the platform, and was keeping to the edge of the fight.  His intent was clearly to be close enough to Faultline's group to possibly tag them, but not so close that one of his uncontrolled blasts would catch a fellow Merchant.



My bugs told me we were close to Lisa, Charlotte, Jaw and Senegal.  I caught Minor's attention and pointed, and he put Bryce down long enough to give me a boost up to the top of the wall that stood between us.  I straddled the wall and waited for Brooks and Minor to figure out how to get Bryce up to me so I could pass him down to the others.



From my vantage point, I could see more of the battle unfolding on the far side of the mall.



One powered Merchant charged Faultline and collapsed through the ground she had strategically weakened.  She kicked him several times in the face before the next member of Skidmark's group tried to take her on, drawing and pointing a gun.  Faultline drew her feet apart, and then dropped through the floor of the platform in a spray of splinters.



To her right, the red-headed woman was striding towards Scrub.  He aimed a shot and missed by a fraction, and she didn't even flinch.  Another try, another miss.  As she got close, he let his power go haywire, and a dozen flashes erupted in close vicinity to him.  None touched her.



She had her gun drawn, but she didn't shoot him.  Instead, she grabbed him by the collar, then wrenched him to one side so he tipped over the side of the platform and fell the twenty or so feet to the ground below.  It wasn't enough of a fall to guarantee that he was out of the fight, but she seemed confident enough to turn away and move on to the next target before he'd even finished falling.



Gregor was keeping up his steady pressure, alternating between blasting Trainwreck and blasting Mush with one hand and aiming at Skidmark with the other.  Skidmark used his power to push away the worst of the slime, but it was clear he was losing.  His power wasn't strong, it didn't have much more push to it than a strong wind.  Any attempt to get it as effective as it had been at the edge of the arena took time and multiple layers of the effect.  In short, Gregor could make the slime more easily than Skidmark could get rid of it.



A knotted bandage tied around Bryce's good arm was thrown up to me, and I used it to draw his arm up while the others managed his lower body.  Once I had his wrist, I gripped it firmly in one hand, my upper body hugging the top of the wall to keep myself from being pulled off.



Minor gave Brooks a boost and the medic straddled the wall facing me.  We worked together to raise the unconscious boy over the top of the wall and pass him down to where the others waited.



I glanced back towards the fight.  Faultline had emerged from beneath the platform and moved around to the side, and using her power to draw hand holds into the side of the platform.  The cape who'd been aiming at her with the gun stooped over the hole she'd dropped into and looked down to see if she was still down there.  He was oblivious as she hauled herself over the edge of the platform and attacked him from behind, striking him with one elbow, then reversing the turn of her body to sweep his legs out from under him with one extended leg.  The sweep of her foot had apparently coincided with a use of her power, because there was a cloud of stone dust as he collapsed onto broken, uneven ground.  From my angle I couldn't see for sure, but I thought maybe he'd fallen head first into the hole she'd first descended into.



Brooks and I hauled Minor over, and I waited while he climbed down, since I was already fairly secure where I was.



Skidmark was losing.  It was obvious from where I sat, and I could see his changing expression as he saw Mush collapse beneath Gregor's sludge and realized he had no friends left.  Gregor, Labyrinth, Faultline and the red-haired woman were all in action, and Skidmark was pretty much alone at this point.



I hadn't seen Newter or Spitfire, and I couldn't be sure if he was okay or not.  Sure, the Merchants could have hit him with weapons rather than their bare hands, but he was quick, he had his tail, and he only needed to touch someone to drug them out of their minds.  Spitfire might be the one babysitting Labyrinth somewhere out of the way.



It had to suck for Skidmark, losing like this.  He'd risen to power based on a streak of good luck and momentum rather than any talent, deed or ability.  Now it was falling apart.  He'd lost, he'd had his ass kicked in front of the bulk of his followers, and he would likely never regain what he'd had.  Not that I felt \emph{bad} for him.  There was a kind of justice to it.



He didn't even have a power that would let him go down in a blaze of glory.  No, his final act here would be one of petty spite.



His power streaked from his hand to the ground where the canisters and metal case sat.  I could see Faultline's expression change behind her mask, saw her set her feet and start sprinting for the case before Skidmark's power even took hold.



The metal box and canisters launched out over the edge of the platform and into the air above the crowd.  Only a few papers escaped the case at first, but his power had saturated the insides of the box.  Just after reaching the apex of its flight, his power seized the contents and the case expelled everything from within.  Papers slid off one another and into the air, forming a small cloud.



``Taylor!'' Lisa shouted.



I knew what she wanted.  I drew clouds of my bugs from the ceiling, catching the papers that weren't saturated with Skidmark's power, collecting my bugs on them.  I could have maybe carried them directly to me with enough bugs, but I found it easier and more discreet to use the bugs and nudge the papers into floating on the air currents, like paper airplanes without the `airplane' aspect of things.



As they got close, I took a firmer hold over them and moved them directly to us.  The papers crumpled as my hands closed around them.  Four or five pages.  I couldn't be sure two might have been stuck together.



``We need an exit,'' I said, as I hopped down from the wall.  I handed Lisa the papers.



Lisa nodded, ``I've been thinking on that.  Look.''



She pointed at one corner of the mall.  It looked like any other section, heavily altered by Labyrinth's powers.  The shops had been almost entirely consumed by Labyrinth's powers, and were further shrouded by the floor-to-ceiling statues of human figures that stuck out of the walls.  In the corner Lisa was pointing at, there were male and female figures, expressions solemn, hands reaching, moving so slowly I might have thought it was my imagination.  The shop below was nearly gone, the entrance nearly covered up.



``Not seeing it,'' I said.



``Look at how they're standing.  The male figure is sticking out of the left wall, reaching with his right hand, the female figure is doing the opposite.  Look past them, at the corner.''



I did.  Between the figures was the point where the two exterior walls of the shopping center joined\ldots nothing jumped out at me.  The walls were bare.



``I don't see it,'' I repeated, as she tugged on my arm and started running forward.  As a group we started moving toward the corner.  ``What am I looking for?''



``Nothing!  There's nothing there because her power isn't extending to that corner.  She's too far away, on the roof at the other side of the mall. Which means the interior of that shop isn't affected by her power!''



However ominous the giant statues were, they didn't react to our passing.  The exit was small, barely three feet across.  If Lisa hadn't given me her reasoning, I wasn't sure I would have had the guts to go through.  It was spooky to think about putting myself in a smaller space like the store interior and having it close tight behind me.



The bodyguards had to go through the doorway in a crouch, and Minor dropped Bryce to let the others drag him inside, just so he could fit.



As Lisa had suggested, the shop interior was largely unaffected by Labyrinth's abilities, though it had been trashed by looters and the effects of Leviathan's attack.  We found the back rooms, and Jaw kicked the door open.  From there, we made our way to the emergency exit, cleared rubble away and escaped into the parking lot.



A handful of others had found escape routes too, I noted.  Merchants were crossing the parking lot at a run, or helping wounded buddies limp away.  We weren't so conspicuous.



I hurt.  I'd been cut on the arm, and I'd taken my lumps in too many other places to count.  My knuckles and fingertips were scratched raw from climbing the walls of the maze and moving rubble, my cheekbone throbbed where I'd been elbowed, and my fucking contact lenses were still irritating.  Never ever something I could get used to, even with other things taking up my attention.



But we'd made it.



We moved at a light jog for a good distance before Brooks called us to a stop.  We lay Bryce down for him to look at, and he decided we needed call for a pickup to get the boy more serious medical attention.



While we waited for the car to arrive, Lisa, and I sat down on a nearby set of stairs.  The other bodyguards were still on duty, still watching for trouble.  Charlotte stood a distance away, hugging herself.  She looked like she wanted to leave, but lacked the courage to go alone.



I was going to go reassure Charlotte, but Lisa retrieved the papers I'd given her and smoothed them out against her leg, and the widening of her eyes caught my attention.



``It's a letter or contract from the people who made the stuff, talking to the guy who'd bought this stuff.  Let's see, we have\ldots page two.  Pages eighteen and nineteen.  Page twenty-seven.  Page sixteen.  Wonder if we can put a narrative together.''



``You probably could,'' I said.



She glanced over one page, then handed it to me as she moved on to the others.  I read it.



client one, and clients two through six for confidentiality purposes.  For clarity, and to help ensure that the proper clients receive the intended products, we must restate facts for client one to double-check.  Client one is the negotiator for each of the clients, guardian of clients two and three and is not intending to consume the product.



This cannot be stressed enough.  Client one is not to share or use any of the product intended for other clients.  Ignoring this warning or failing to adhere to any other warnings or directions within this documentation will compel Cauldron to carry out the countermeasures and call in all debts noted in sections 8b and 8c on pages seventeen, eighteen and nineteen.



Clients two through six are noted here in as much detail as is allowed given the agreed-upon confidentiality.
\sectionbreak  Client two is the elder of client one's two relatives noted here, female.
\sectionbreak  Client three is the younger of client one's two relatives noted here, male.
\sectionbreak  Clients four and five are client two's friends.  Client four is female.  Client five is male.
\sectionbreak  Client six is the friend of client three, male.
Both vials and protective containers are noted with the numbers specific to each client, each containing the requested upon products from the catalogue.



I wish to give written evidence of the verbal exchange between Cauldron and client one on February 18 2011.  Client one is informed that client four scored a borderline failure on the psychological testing and that results may lead to a Deviation scenario



``What's on the other pages?'' I asked.



``Sixteen is accounting.  Bank statements, confirmation of money exchanged, a list of what was bought.  Seven figures base price, more for this Nemesis program, still more for some powers.  Don't have all the pages I'd need to get it, but I'm getting the sense the more unique powers and the stronger ones cost way more.''



`The sense', she'd said.  Her power filling in the blanks.



``Pages eighteen and nineteen refer back to something called the `Nemesis program', potentially revoking it, they're talking about debts, services required by this `Cauldron' using the clients' powers.  There's a bunch of specifics on how the time, effort and risk of said services would factor in with one another.''



``People can buy powers?  How many people are doing this?''  I felt a touch offended at the idea.  I'd \emph{earned} my powers through my hardships.  Most of us had.



``Enough that there's a whole enterprise here with a private army.  There's this bit that very politely notes that breaking the rules will get you hunted down and executed by Subjects, capital S.  Clients are warned that these guys are entirely loyal to Cauldron, will not accept bribes.  And these Subjects are apparently something different from Deviations.''



``Cauldron calls us Subjects.  The PRT calls us Case 53s,'' a voice said from above us.  ``Regular people call us monsters.''



Our bodyguards wheeled on the spot, a set of guns training on Newter, where he clung to the side of the building.  They had been covering the possible approach points from the ground.  They hadn't been expecting trouble from directly above us.



``I heard of the Case 53 thing,'' Lisa told him, backing away.  ``The rest is new.  You work for them?  No.  But you're related to this.''



``Gregor, Shamrock and I were test subjects.  Guinea pigs to test the new formulas, so the buyers don't get fucked.  According to Shamrock, three in five of us don't even survive.  One in five Subjects are retained and brainwashed so they can protect the business and enforce the contracts.  Shamrock was going to be one of them, but she escaped.  The rest of us have our memories removed, and we're released as part of the `Nemesis program.'''



``Which is?''



Newter glanced at the papers, ``I'd really like to know.''



``So you followed us.''



``Something about the way that one moved,'' Newter pointed at Jaw with his tail, ``Reminded me of some other mercenaries I've come across.  Don't bother shooting, by the way, I'm too quick.''



Lisa gestured, and the bodyguards lowered their weapons.



Newter frowned, ``I gathered you were mercenaries, decided to spy, but finding you'd taken the papers was a surprise.  Who are you?''



Lisa looked at me, without a ready answer for once.  I looked over at Charlotte and sighed.  She'd already put some of the pieces together.  She could probably figure it out from here.  I might as well control when that happened, so I wouldn't get caught off guard further down the road.



I raised the piece of paper, as if to hand it to Newter, and I directed bugs to cluster on it.  In moments, the half of the paper closest to him was dark with various flies and creepy crawlies.



Charlotte's eyes widened.  This was apparently her putting the last piece into place.



``Ah, Skitter,'' he said.  Apparently my having saved his life once and gifting him a paper bag filled with money didn't do much to ease his wariness.  He wasn't any less guarded when he asked, ``Why are you here?''



I pointed at the unconscious Bryce.  ``An errand.  Didn't mean to get in your way.  I only grabbed the papers as a spur of the moment thing, and because they would've been ruined if they'd just drifted all over in there.''



``That wasn't much of a concern.  One of my teammates is collecting the papers as we talk, and I expect she'll find nearly all of them.  The ones that she could find with some luck, anyways.''



``We're honestly not looking for trouble, and  I have no problem with giving you these.'' I banished the bugs on the paper and stepped forward to extend it towards him.



Lisa followed my cue, offering the others, ``Wouldn't mind copies of whatever you've got.''



Newter frowned.



Before he could say anything, Lisa hurried to add, ``I'm good at figuring stuff out.  I'm a fountain of knowledge.  I want to know more about this stuff, and I could help you guys in exchange for what you've already got.''



``I'd have to ask Faultline.  She doesn't like you.''



Lisa grinned.  ``And I don't like her.  But she's not stupid, either.  She knows this is mutually beneficial.''  Lisa drew a pen from her pocket and scribbled on the back of one page.  ``My number, if you're interested.''



He took the sheets, looked them over, then rolled them up and stuck them in his back pants pocket.



``We'll be in touch one way or another,'' he said.



Then he was gone, around the side of the building and up to the roof in heartbeats.



I looked at Charlotte, and she shrank back, as if I could hurt her by looking at her.



Which was dumb.  It was fairly obvious to anyone who considered my power that I didn't need to look at people to hurt them.  Not that I'd hurt her, anyways.  She'd done nothing to deserve any such thing, beyond being in the wrong place at the wrong time.



Charlotte, Bryce and Sierra.  The civilians.  I still had to figure out how to deal with them.  My heart sank.  Social interaction: not where my talents lay.





