





I could see Dr. Q grow more irritated with every person that filed into the office.



Ten people in total.  There were the eight that we'd all packed into the car and fake ambulance Coil had sent.  Lisa, me, Bryce, Charlotte, Minor, Senegal, Jaw and Brooks.  Two more, our drivers, had stepped in to verify everything was okay before leaving to stand guard outside the front of the building.



The good doctor took one look at our group, ordered us to put Bryce on the first bed, then sighed and said he'd patch the rest of us up when he was done with the boy.  Lisa suggested me for the next in line, which means I was made to sit down on the bed in the far corner.  It wound up working out on several levels, because it gave Lisa a chance to talk privately with Minor, and it gave me a chance to have words with Charlotte.



Dr. Q ordered the remainder of Minor's squad to leave until they were called in, which meant there were more people standing guard outside.  I wondered if it was reaching the point where the guards would attract more problems just by virtue of drawing attention to themselves than we'd face otherwise.



Charlotte looked spooked.  Maybe rightly so.  She had to be aware that she was privy to information and details to a degree that we couldn't just let her go.



I moved into a cross legged position on the bed, adjusting the pillow behind me to keep the headboard from rubbing against my back.  I pointed, and told Charlottte, ``Sit.''



She obeyed, but she sat on the edge with her legs dangling, her body twisted to face me, as if she wanted to be able to run at a moment's notice.



After some consideration, I frowned and told her, ``I don't know what to do with you.''



``You don't need to do anything?'' She made it a question, a request.



``You're the first person who knew me that knows about this.''  I paused.  ``Or knew \emph{of} me.''



She looked down at her hands, ``I- I don't\ldots I didn't see anything.''



``Charlotte,'' I frowned, ``Look up at me.  Meet my eyes.''



Reluctantly, she did.



``I'm not stupid,'' I told her.  ``And as cute as that whole cliche is, you and I both know you saw everything.  This is serious.''



She looked at the scene to our left, the doctor, Bryce, Lisa and Minor.  Leaning towards me, she whispered, almost plaintive, ``\emph{Why did you bring me here}?''



``Because you'd already seen too much.  There was no avoiding it.  We couldn't hide it from you without leaving you behind, and neither of us wanted that to happen, right?''



She shook her head with a glum expression on her face.



Seeing that, I answered her question from before, ``I brought you here because I wanted you to know that our group isn't just a few kids in costumes running around.  We're an \emph{organization}.''



``I don't want to know this!'' she said, clutching her pants leg in her hands.



``You need to,'' I started.  I was about to go on to say something more, but I was distracted as another group of soldiers entered the room.  They carried a white cooler between them, and set it at Bryce's bedside. I lost my train of thought as I watched to see if Bryce was okay.



The cooler was opened, and bags of blood were hung on the wall beside Bryce.  Once that was done, the soldiers wordlessly carried the cooler out the door.



I sighed, ``Look, Charlotte, I'm not your enemy.''



``You saved my life,'' she said.



``That's maybe an exaggeration.  I saved you from being assaulted by those men, probably-''



I could see her shrink into herself.



``-I'm sorry.''  I finished, lamely.



``You're a villain,'' she said, and it took me a second to realize it was more of a non-sequitor than an admonishment for reminding her of what had nearly happened to her.



``I'm a villain,'' I agreed.



``And you're going to tell me that if I ever open my mouth, you'll kill me.''



``That \emph{is} one option.  Or, theoretically speaking, I could hurt you or your loved ones.''



She deflated, which was pretty impressive given that she hadn't exactly been brimming with vigor before I'd opened my mouth.  It was like she didn't even have the energy to be afraid.



``I'm \emph{not} going that route,'' I told her, ``I don't want to be that kind of bad guy.''



She looked up at me.



``I'm improvising, and you're going to have to forgive me if my ideas are a little rough around the edges\ldots but two ideas spring to mind.  Number one is that you leave.  I'm offering you an out.''



``Leave?  The city?''



I nodded.  ``Leave Brockton Bay.  You have any family here?''



``My mom.  She's doing the training to join the construction crews.''



``You'd leave the city with your mom.  Put all this behind you, the ruined city, what happened at the mall, \emph{me}, everything.''



``And I wouldn't say anything,'' she finished my thought.



``Right.  You'd keep your mouth shut.  Because if you did start discussing stuff you shouldn't know?  Those soldiers, the hackers, the plants we have with police and FBI and government?  My psychic friend over there?  They'd find you.''



I could see her clutch her pants leg a little tighter.



``And believe me, Charlotte, I don't want to hurt you.  But it would be out of my hands.  I'm not the top dog here.  The person in charge?  \emph{They} would handle things after that.  Understand?  They would handle \emph{you}.''



``I'm not saying anything.  Really.''



``I know.  And I know you wouldn't say anything even hinting at what you know, unless it was to a therapist and you were absolutely sure it was confidential.  That's what I'm proposing.''



Her head hung, ``I\ldots don't think I can leave like that.  I wanted to, before all of this, but my \emph{zaydee}, my grandpa, he refuses to leave, and he can't take care of himself when the city's like this.  It's why we didn't evacuate.''



``You could tell your mom and grandpa some of what happened.  That the Merchants got you, that you got away, that you don't feel safe here.''



She buried her face in her knees.  ``No.''



``Okay.  So that leaves option two.''



``I-'' she started.  She stopped when I raised one hand.



``Don't say anything until I explain it.  I'll forget what I want to say if I get distracted.  You're going to work for me.  And every doubt and possibility that just made you tense up at that idea?  It's not going to happen.  You'll be safe.  Safer than you were before.  You won't have to do anything illegal unless you're willing.''



``I'd still be helping you, I'd be helping a criminal, indirectly.''



``You would.  But I think you'd be surprised at my approach.  I'm not looking to hurt innocents.  I'm not pushing hard drugs, I'm not demanding protection money.''



``Then what are you doing?''



Funny, how everything always seemed to tie back to the beginning.  I was put in mind of the conversation I'd had with the Undersiders on our second meeting.  The same conversation that had led to me joining them.



``I'm afraid the full details only come with membership,'' I echoed Lisa's words to me from back then.



``I don't really have much of a choice, do I?''



``You do.  More than you think.  Don't give me a response just yet.  Think about it for a bit.  You're staying at least until you get those scrapes and scratches looked at.''



Charlotte looked at her hands.  Her knuckles and fingertips were torn up, and she had a shallow cut on the side of her neck.  ``This isn't anything worth worrying about.''



``The way this city is right now?  You'll get an infection if you don't get that taken care of.  Relax.  Believe it or not, you're safer right here, right now, than you've been for the past few weeks.  Breathe, think about what you want to do.''



She glanced around, and I could tell she didn't believe me.  Still, she met my eyes and offered me a nod.



Well, I hadn't solved the Charlotte problem just yet, but I'd at least addressed it.  If I was honest with myself, part of the reason I told her to wait on her answer was to buy myself a reprieve, give myself time to think.



Maybe that was a bad idea, because being left to ponder let the anxiety build up.  I was worried.  Not just about Charlotte, but about my territory.  Had the Merchants attacked it in the meantime?  Lisa had said they would mostly be at the party, but I couldn't be absolutely sure.  Grue would have been watching it for me, but he'd be tired, and he didn't have the same awareness over the area that I did.



I almost regretted leaving for this, for Bryce, even though I knew I'd do it again.



If anything calmed me down, it was seeing Lisa with the two squad leaders.  She laughed a little, and put her hand on the arm of the other squad captain, Fish.  When she caught me looking her way, she smiled and gave me a wink.



When Dr. Q had done everything he could for Bryce, he turned his attentions to me.  I got more stitches, in my arm this time, which was fun.  I also got to see every single one of my cuts and scrapes fizz with foam as he disinfected my injuries, which stung like hell.



He was nearly done when a knock came at the door.  Jaw was on the other side, and he was escorting Sierra, as I'd requested.  She went immediately to Bryce's bedside.



``His hand,'' she said.



``Things got violent,'' Lisa said, stepping towards her.  ``We didn't start it, but they got ugly.''



Sierra nodded mutely, then turned to Bryce.  She knelt at the side of the bed and held his intact hand.



``I'm sorry,'' Lisa said.



Sierra shook her head, her dreadlocks swinging, ``No.  I understand.  The hand isn't your fault.  He's here and he's alive because of you.''



``No.  I'm sorry because I have something to tell you that's going to be hard to hear.  But you need to know this.''



Sierra looked up, her brow creased in concern, ``Did they drug him?  Dirty needles?  Did they\ldots was he-''



``They didn't touch him,'' Lisa reassured Sierra, ``But that's because he wasn't one of their victims.  He was one of them.''



Sierra shook her head, ``No.  You must have misunderstood.''



``The people who attacked the church?  He was with them.  He got hurt helping them fight to win some prize the leaders were offering.''



``No,'' Sierra shook her head again.  ``He wouldn't!''



Lisa shrugged, unable to find the words to convince her.



Sierra sounded angry now.  She stood, confronting Lisa, ``No!  Where's Skitter?  Where's your boss?''



I hesitated.  My secret identity, such as it was, was already falling apart.  It wasn't that I was \emph{that} committed to it, since I wasn't `Taylor' that much of the time these days, but there was always that worry in the back of my mind that I was burning my bridges as far as being able to go back home, or that I was possibly giving out clues that someone could use to trace back to my dad and hurt him.



On the other hand, I could see how Sierra was on the verge of losing it.  I couldn't tell if she was going to cry, hit Lisa or say something she shouldn't, but I couldn't let her do anything that would get her in trouble with the soldiers.  I stood from the bed.



``Sierra,'' I called out.



She wheeled on me.  I watched her expression change as she stared at me and realized who I was.



``You got hurt,'' she said, looking almost stunned by that realization.  How bad did I look, that my injuries distracted her from her brother?  Or was it the realization that a supervillain \emph{could} get hurt?



``Things got ugly,'' I said.  Then I added, with emphasis, ``Lisa wasn't lying.''



She shook her head, ``It doesn't make any sense.  He wouldn't do that.  It doesn't fit with the guy I grew up with, ate dinner with.''



Lisa spoke from behind her, ``His parents were in the hospital, his home and school was gone, and he was a scared, confused kid that was offered a community and the power to change things.  It's like what cults do.  They prey on people who are at their most vulnerable, people who are lost, with no attachments, who are hungry and weak.  It's easy to underestimate how readily they can get to someone.''



``Fuck!''  Sierra turned to kick the side of Bryce's bed. ``Is that supposed to be an excuse?  No way he gets off that easy!  He joined them, you said!  He wasn't brainwashed when he fucking decided to go with him!''  She kicked the bed again, hard enough that it shifted an inch or two away from her.



I could see the Doctor start forward in response to the assault on his furniture and patient, but Minor, Jaw and Fish moved first.



``Guys, stop,'' I ordered.



They did.  It was kind of strange, to have people listening to me.  Sierra turned and saw the soldiers, and I could see emotions flicker across her face.



``He's not getting off easy,'' I said, ``He lost most of his hand.  I'm not a doctor, but he might lose the rest, depending on how the circulation is.''



``He'll lose his remaining fingers, keep the thumb,'' the Doctor spoke.



``So he'll have the rest of his life with that as a reminder of his bad call,'' I told her.  ``The real question is what we do with him.''



Sierra was so focused on the responsibility, the blame and the betrayal that I think it took her a few seconds to process the problems that came with getting her brother back.  I could see it hit her, the idea that she might have to repeat the experience of losing her brother, with all of the same pain and worry, the moment he got a chance to slip away.



Dr. Q apparently didn't care about the drama.  Once he was more or less confident that Sierra wouldn't be disturbing his patient, he got up and walked over to Charlotte to start patching up the girl.  I walked over to Sierra and led her away from her brother's bedside to the far corner of the room, next to Charlotte and the doctor, where she wasn't getting in anyone's way.



``Can you keep him?'' she asked, as we stopped.



``Can I offer him a bed?  Theoretically.  But he's just going to run.  Not that there's anywhere for him to run to, but-''



I stopped as I saw a confused expression on her face.



``The Merchants may be done for.''



``Because of you?''



I shook my head, ``Someone else.  The leaders got pretty badly embarassed, they may have trouble getting their followers to respect them after getting their asses kicked like they did.  The actual criminals would still be on the streets, probably, but they won't be as organized.  Add infighting, rival groups, greed\ldots they won't be as focused.''



``But that girl said my brother was with the people from the Church, he could find them, or they could find him.''



``They're not a consideration any more,'' I told her.



Her eyes widened.  ``Because of what I asked you to do?''



What was the proper response, here?  I felt like anything I told her might offend her.  If I said yes, would she be horrified?  If I said no, would she see it as a failure on my part?



``In small part because of that, yes,'' I admitted, leaving it vague.



Her forehead creased in a frown.



``Look,'' I admitted, ``I need to get back to my territory.  If you need a place to stay, you're welcome to come with, but we \emph{do} need to decide what to do with Bryce.''



``Can you keep him prisoner?  Until he comes to his senses?'



``I would if I thought it would do any good.  He's only going to get angry and resentful at being locked up, and he'll be all the more eager to run.''



``But he's going to run anyways.''



``Probably.  He won't believe me if I tell him about his buddies.''  \emph{It doesn't help that Lisa lied to him about Sierra}.



``So what do we do?''



I was at a loss for an answer.  I turned and called across the room, ``Lisa!''



She broke away from her conversation with Minor and Fish to join us.  ```Sup?''



``We're worried the kid will run.  You have any ideas on what would work?''



She shrugged. ``What if you give him what he wants?''



``Which is?''



``He wants excitement, he wants to feel like a grown up, he wants respect, and maybe a bit of power at a time in his life he maybe feels pretty powerless, what with losing his house, his family, his safety, all that.''



``Okay.  And we do this by?''



``With your okay, I'd recruit him.''



``That sounds like a monumentally bad idea,'' I admitted.



``The soldiers there can keep him in line.  I'll keep him away from Senegal and Brooks.  Minor, Pritt and Jaw could watch him and instill some discipline in him, and they're uniquely equipped to track him down if he tries to slip away.  I'd keep him out of trouble, and have him gather information and act as a pair of eyes on the street.  He'll hate it at first, with the soldiers giving him a hard time, on top of the missing hand, but I think he'll take to it once he's actually doing something concrete.  What kid doesn't want to be a secret agent?''



I had my doubts, but I didn't want to shoot Lisa's idea down.  So I looked to Sierra and asked, ``Thoughts?''



She frowned.  ``Can it be temporary?  I don't want him to be locked into anything even after schools get going again and we're trying to get things normal again.''



``It can be temporary,'' Lisa assured her.



``He doesn't get hurt.''



``He'll have one of those guys with him ninety percent of the time,'' Lisa said, pointing to Minor, Jaw and Fish.



I saw Sierra look at me, noting my injuries, and I knew exactly what she was thinking.  Still, she kept her mouth shut on that particular topic.  ``Okay.  But I join too, so I can keep an eye on him.''



``I'd love to take on another recruit,'' Lisa smiled.  She turned to me, ``But she saw you first.''



Sierra looked between the two of us, then asked Lisa, ``You don't work for Skitter?''



``Partners, believe it or not,'' Lisa replied.  ``We're controlling different territories.''



``Oh.  Two territories.''



``Nine,'' Lisa corrected her.  ``Nine villains, nine territories.  The city isn't getting better and the people in charge aren't up to the task, so we're taking over.''



``You're trying to fix things?''



``Some of us.  Most of us.  Some of us want to help, like Skitter there, and others are doing it because we know that when things are up and running again, we're going to be a part of the status quo.''  Lisa grinned.



I spoke up, ``That's the basic idea of what we're doing.  You heard what I said to the people in my territory.  I'm trying to get people fed, I want them safe, and I wanted to help you and your brother.  If you're working for me, that's the sort of thing you're going to be helping me with.''



Sierra shook her head, ``I only said I'd join because I wanted to keep an eye on my brother.''



Lisa shrugged, ``Then I'll make you a deal.  You join Skitter's group, and I'll give you a contact number.  Whoever is babysitting Bryce will have the answering phone, to give you an update on your brother, anytime, anywhere.  Or put you on the phone with him, if that's what you want.''



``That's not-''



``It's not perfect, no.  But Skitter's probably going to let you head into my territory to see Bryce any time you want-''



``Definitely,'' I interjected.



``-and not to put too fine a point on it, but the guilt over betraying you, coupled with resentment, and the fact that he's in this rebel-against-your-parents phase and you're the closest thing he has to a parent right now? It's maybe best if you give him his space.''



I saw the faintest change in Sierra's facial expression, saw her look over at Bryce, her eyebrows drawing together.  Lisa's words had hurt her.  They'd been true, no doubt, but I had to find a way of gently suggesting that Lisa take a gentler approach.



``Okay,'' Sierra said to me.  ``But I can leave any time.''



``You can,'' I replied.



``And I will, the moment you break our deal, or the moment Bryce gets hurt.''



``I believe you.''



She stuck out her hand to me and I shook it.



``Now go,'' Lisa said, ``I'll send Sierra your way with one of my boys, when she's done visiting Bryce and seeing that he's settled in.  I know you're itching to check on your territory.''



I nodded.  ``Thank you.  For the help finding Bryce, for making this work, here.''



She grinned and waved a hand at me, ``No problem, no problem.''



I gave Lisa a quick hug before heading over to Charlotte.



There was no negotiation.  She was close enough to have heard some of our conversation, and she'd seen the bit with Sierra, besides.  Whatever it was, it seemed to have grounded her.  She didn't look as uncertain as before, and she had one hand extended for me to shake.



``You sure?''



``Yeah.''



``Because really, you can leave the city.''



She shook her head, ``My grandfather needs to stay.  He's spent the latter half of his life in his home, and I think it would kill him to leave.''



``If you're sure,'' I told her.  She nodded.



I shook her hand.



\sectionbreak



``Grue?'' I hollered into my lair, as Charlotte and I stepped inside.  ``Mask on!  Got a guest here!''



Despite Lisa's relatively cavalier attitude on the subject and my own concessions, there was no point in spoiling \emph{his} secret identity, too.



``Right!'' he called down from upstairs.  In a moment, he came down the stairs, his helmet on.  He stopped as he saw me, ``What happened?''



``Bit of a scuffle.''  I replied.  I'd had a chance to see myself in the mirror.  The bruise on my cheekbone had been a nice mottled yellow-green.  I asked, ``Any trouble?''



He shook his head.  He wasn't smothered in darkness, so his voice was normal as he said, ``Quiet.  Was your errand successful, at least?''



``Successful enough.  This is Charlotte, one of my new\ldots employees.'' What was I supposed to call them?  Henchmen, employees, minions?



``Already recruiting?'' he whistled, low.



``Two new hires.  The other girl's going to be on her way in a while.''



``You've gotta slow down.  I only heard what you'd done to take control here after I'd arrived.  I was worried you'd provoked a war and left me to handle things, until Lisa told me the major threats were occupied elsewhere.''



``Sorry.''



``Seriously, you're moving fast on this.  Imp and I have only just started rooting out the gangs and other criminals in our territory.  We haven't even talked about who we're going to recruit or how.''



``I'll explain later?''



``You don't have to.''



``I \emph{want} to.  Just\ldots later.''



``I'm getting the feeling I'm in the way,'' Charlotte spoke up, ``Is there any place I can go to get out of your hair?''



``Kitchen, if you're hungry, or-''  I stopped as she practically lit up at the suggestion.  I pointed at the kitchen, ``Go.  Take whatever, enjoy.''



It was gratifying to see her glee as she started rifling through the cabinets to find piles of stuff ranging from treats to dry pasta to cases of soda.  Grue and I migrated to the empty room that had held the supply crates, where we were able to see Charlotte but not necessarily in earshot.



``If you're pushing yourself this hard to prove yourself to me-``



``It's not that.''



``Okay.  But really, you don't need to prove yourself.  You know Tattletale just called me on the phone?  Ten minutes ago?''



Ten minutes ago, I would've just left the doctor's place, en route for my lair with Charlotte.  I frowned.  ``What did she say?''



``Chewed me out big time, about how I was being too hard on you, after the\ldots revelations at the hospital, about turning you down.  Calling me a clod, basically.''



I felt a flush warm my ears.  ``I told her not to interfere.''



``Well, she did, and I think she was right to.  I've been a bit hard headed.''



I shrugged.  Couldn't agree without offending him, but I didn't disagree either.   I'd been stubborn in my own ways too.



He asked, ``So do you want to call it even?  I said it before, but I thought maybe we could become best friends, somewhere down the line.  I'd like to go there again, if you're willing.  If it's not awkward or-``



I felt the flush deepen and hurried to interrupt him before he could bring up my asinine confession again, ``It's good.  Yes.  Let's go with that.''



``Good.''  He clapped one hand on my shoulder.  A sign of camraderie, friendship, with the subtle effect of reinforcing that I was at arm's length.  Or was I reading too much into things?



I could live with it.  It was worlds better than the quiet hostility and hurt I'd been sensing from him as of late.



``Is it cool if I drop by sometime?'' he asked.  ``So we can keep each other up to date, or maybe just hang out?''



``Hanging sounds good,'' I answered him, feeling lame as I said it.



``I'm gonna go sleep.  Long day.  You take care of yourself, alright?'' he said by way of a goodbye as he headed for the door.



I nodded, ``You too.''



When I walked over to the kitchen, Charlotte had a box of toaster strudels in one hand and a package of cookie dough in the other.  She'd washed her face, and only trace amounts of the caked-on makeup were still there.  She looked worlds younger, and was like a little kid as she asked me, ``Can I use your oven?''



``Go for it.  But I get some,'' I smiled.



As my new minion set about figuring out the oven, I was able to stop for a moment.  Doubts and insecurities still weighed on me, but I couldn't feel guilty for not making more progress today.  I'd done what I could to move forward on my plan to help Dinah.  Both Lisa and Brian had acknowledged that I was making great strides forward, and that gave me hope that I might be impressing Coil as well.



Things weren't perfect, but they were \emph{better}.  I was on speaking terms with Brian, I was making headway on my plans, Lisa was making headway on her end of things, and in some small way, I felt like I'd finally followed through with that dream I'd had at the start of the year, of being a superhero.



I was a villain.  I'd given the order to let a man die.   Maybe my abandonment of Thomas would weigh on my conscience more after I got some sleep and my thoughts were clearer.  Maybe not.  But I'd also done something to help people, without ulterior motives.   I'd given Sierra her brother back, I'd saved Charlotte.  I was happy about that.



All in all?  If I didn't think too hard about it?  I could feel cautiously optimistic for the first time in a long while.  For the first time in weeks, months, I could feel like everything just might work out.





