





A howl tore through the air.  It wasn't the howl one would expect from a dog.  It was ragged, with a guttural undertone that hinted at the size of the one doing the howling.



Before the howl had even finished, more took up the cry in answer.  A second howl, then a third.  More joining in, all at once.  Seven or eight.



Bentley raised his head and joined them, his tail wagging on his undersized hindquarters, almost prancing on the spot in his excitement.  Water splashed around paws as wide around as bike tires as he landed, spraying Bitch.



His enthusiasm was infectious.  She bared her teeth in a wide grin, then whooped, adding her voice to the cacophony.  She hopped up his side, gripping ridges of hard muscle and bony growths so she could throw one leg over his other shoulder.  A spike of bone scratched her upper thigh, beneath her skirt, but she didn't care.  It was nothing.



``Go, Bentley!'' She urged him.  He surged forward like an arrow loosed from a bow.



She could feel the heat of his body underneath her, the rippling movements of his muscles as he ran.  She could smell him, like dog breath and the coppery tang of blood, that faint sweet smell of meat on the verge of going bad.  She could smell herself, her body odor.  She hadn't washed in two days, but she liked her own smell.  She liked that her belongings and her place all smelled like her.



It wasn't that she wouldn't take care of herself.  She would, just like she took care of her dogs.  Just as she groomed each of them twice a week or more, she would tend to herself.  But what did some scruff on her legs matter when she was treading down flooded streets or caked in mud up to her knees half the time anyways?  What did some body odor mean, if she didn't even \emph{like} the people who were around to be offended by it?



Barker, Biter and the others would be at the locations she had assigned them.  She had given them the most menial of tasks.  Grooming the dogs, feeding the dogs, picking up shit, checking the dogs for sores, cuts, ear infections and ticks like she'd showed them.  She had a good number of dogs in her care, now.  Most had been taken from kennels that hadn't been in a state to help the animals since Leviathan attacked.  She was eagerly anticipating the moment someone complained.



Barker or Biter would be the ones to whine about the task first.  They had powers.  They had expected to be in charge, to be her lieutenants.  The looks on their faces when she'd given them their tasks had made her day.  Nothing like putting someone in their place.



If they didn't complain by the time they were through checking and taking care of all of her dogs, maybe they would start when the next batch arrived from the shelters, and they were told they had to do all of those dogs on top of starting afresh with all the ones they had done before.



The moment someone \emph{did} complain?  Or if they let \emph{one} tick, one rash or one ear infection slip?  She could make an example of them.  Humiliate them, scare them, insult them.  If she did it well enough, they'd leave.



If she did it really well, they would \emph{all} leave.



Then she could be alone for a while, alone with her dogs.  Nobody would be able to nag her about the fact that she hadn't given the henchman thing a try.  Fuck it.  She already\emph{ had} all of the assistance she needed.  The best, most loyal kind.



Lucy appeared from a nearby street, making her excitement known with a noise that was half bark and half something else.  She ran alongside Bentley.



``Good girl!''  Bitch laughed, ``Come on!''



Lucy responded by huffing out a noise that might have been a bark.  Her footfalls splashed out of sync with Bentley's, and they were soon joined by others.  Ink, Magic, Roxy, Buddy, Bruno and Socks.  None of the others were as large as Lucy and Bentley.  This would be their first run.  A taste of her power.  She would give them a little more each time, keep an eye out for the ones who listened, give more training to the ones who needed to be kept in line by the bigger and more obedient dogs.



But this was her territory.  Her space.  Finally a place where she could do what she wanted.  Here, she was free, and that meant she could be dirty.  She could go where she wanted, hurt anyone who got in her face.  She could roam free with her dogs and try her power on them without worrying about people getting hurt.



Which wasn't to say that people wouldn't get hurt, of course.  Just that it was her territory, and she was allowed to make the call.  Anyone who hadn't gotten the message already deserved what they got.



Bentley and the rest of her pack drew towards the source of the howling.  Sirius stood outside an apartment block, filling the evening with that mournful, haunting sound that carried through the air.



She hopped down from Bentley's back, and used the back of her hand to wipe away some of the sweat, mucus and blood that had transferred from his back to her inner thigh.  ``Sirius!  Good boy!''



He wagged his tail, and the tip of it made trails in the water.



``Sirius, guard!'' she pointed toward the front door of the building.  ``Bentley!  Guard!'' She pointed at the little emergency exit at the side.  The two dogs moved to their respective positions.



``Sit!''  Her dogs all sat.  She noted Magic was a little slower than the rest to obey.  Would Magic have listened if the other dogs hadn't been here?  If she hadn't been following along with the others?  Bitch made a mental note.



``Stay\ldots'' she ordered, drawing out the word.  She could see the group of dogs freeze.



She had a routine with her dogs.  The first priority was making sure they were healthy.  That meant grooming and possibly shaving them, getting their records and shots updated if they hadn't come from the shelter, cleaning their ears, and ensuring they were kept away from the other dogs so she could check the color and consistency of their shit and track any changes.  Shit revealed a lot about the dog it came from, from the obvious of diet to general health to mood.  An unhappy dog had unhealthy shit.



The second step was training, and every dog got some dedicated attention.  `Sit' was the first command they learned, followed closely by `stay', `off', `fetch' and `come'.  Depending on the dog, it could take a couple of days before they had it down solid.  These commands were absolutes.  If a dog didn't listen to each of those, it wasn't allowed to go out, and it didn't get any use of her power.



Once a dog had those commands down, it opened the door to other orders.  A dog that would stay put while she demonstrated with another would be that much more inclined to follow suit.



If only humans were as reliable, as easy to train.



``Dogs, attack.''  The word was quiet, but every dog present was waiting for it.  Bentley and Sirius stayed at their positions, but the rest of the dogs surged into the building, the larger ones leaping through the boarded up windows, the smaller ones surging in the front door.  Growls and barks that were twisted by the unnatural shapes of their throats overlapped into a single noise.



She waited outside the building, one hand on Bentley's neck.  He wanted to go, she knew it from the tension, but he was obedient.  Good.  This was a test for him.



Another howl sounded, far away, startling her.  If her dogs were here with her\ldots oh.  Only one dog would be elsewhere.  She listened as the howl came again.  Yes.  Angelica's howl reflected her size and the degree to which Bitch had used her power on her.  More than Bentley, Sirius and Lucy.



She whistled for them to come back, long and loud, and her dogs came tearing back through the building.  She checked, and she couldn't make out any blood that didn't belong to the dogs.  Good.  Better to terrorize and inflict light wounds than to maim or murder.  If the people in that building stayed in her territory, she would be surprised.



She climbed onto Bentley's back, then whistled twice.  \emph{Come}.



A jerk of the chain collar around Bentley's neck and a kick to his sides spurred him into action.  The others followed, some yipping or barking with excitement.



Did other people experience anything close to this?  Did Taylor, Brian, Lisa or Alec?  She felt like she was one with Bentley as she caught quick breaths between his jarring footfalls.  Water splashed onto her skin and his.  Her legs pressed against his body, and she could feel the expansion and contraction as he huffed out breaths.  She trusted him, and he trusted her absolutely in return.  It varied from one dog to the next, but the same was true with the others that were following in Bentley's wake.  They believed in her, and if they didn't love her yet, she knew it would come in time, with her patience and continued care of them. What did Lisa have that compared to that rush, this security?  What did the others have?



\emph{Why}, Bitch wondered, \emph{are they happier than me}?



Unbidden, the answers came to mind.



She remembered living with her mother.  She couldn't even remember the woman's face, but that was little surprise.  Mom had worked anywhere from three jobs to none, but she spent little time in the apartment.  When she \emph{was} home, she was either drinking in her room or partying with friends.  Little Rachel's questions or attempts to get attention were met with anger, rejection.  She would be pushed away or locked in her room.  Better to stay quiet, watch for an opportunity.  If her mother passed out drunk, bills could be taken from her wallet, secreted away for later purchases of bread, peanut butter and jam, milk and cereal or orange juice at the corner store.  If there was a party, and if she was successful in keeping from getting underfoot, she could often snatch a bag of chips, a box of ribs or chicken wings, to eat under her bed or on the roof.



So she got by.  Until the day her mother didn't come home.  The food in the cupboards had disappeared, even the cans of pineapple, pears and nuts in foul-tasting syrup that had been left behind by the apartment's previous residents.  Desperate, terrified to leave the apartment in case the fifteen minutes she spent looking for food were the same fifteen minutes her mother stopped by, she'd turned to trying to cook the rice, standing on a chair to reach the sink and stove-top.  After pouring the rice into the water that had been sitting on the hot stove, she'd accidentally brought her arm down on the arm of the pot, and tipped it all over herself.  In retrospect, it was a blessing that she hadn't known that the water should be boiling.  Still, it was hot enough to turn her skin pink and leave her screaming enough to drive the neighbors to call nine-one-one.



Then the foster homes.  Home one, where the parents were kind, but lacked the patience to deal with a little girl who child protective services had labeled a borderline feral child.  Her foster-sister there had been a \emph{mongoloid} that stole things, breaking or ruining what she couldn't take for herself.  Rachel had responded the only option she could think of, attacking the girl who was three years older and fifty pounds heavier, leaving the girl bloody and sobbing.



They found a new home for her rather quickly, after that.



Home two, where the parents were not kind, and she had four foster siblings rather than the one.  Three years there, a long series of lessons on what she'd done to the idiot sister from the first home, taught with the roles reversed.  An education in violence of every kind.



Unable to keep the feelings bottled up within her, she screamed until she couldn't breathe any longer.  Then she took a deep breath and screamed again.  Even though she screamed until it hurt, it was tiny and insignificant compared to everything she wanted to convey.



Home three had been the breaking point.  Two foster siblings, a single foster-mother.  She'd overheard her caseworker saying that the new foster-mother would be a disciplinarian, the only person that might be able to turn Rachel into a civilized human being.  Bitch's opinion, years later, was that this had been a retaliation, a punishment inflicted on her by the caseworker for the countless trips to school or the home to deal with Rachel.



She hadn't believed that her foster mother could be more of a disciplinarian than her second set of foster parents.  Realizing the nature of her situation had been unpleasant.  The foster-mother brooked no nonsense, and had a keen eye for every failing and mistake on her children's part, quick to punish, quick to correct.  If one of her children spoke with their mouths full, she would snatch that child's plate away and dispose of the contents into the trash can.  Never the carrot, always sticks.  Rachel was made to attend school, then after-school make up classes, with piano every other day, as if she couldn't be bad if she didn't have the time.



But Rachel hadn't been equipped for these things, would never be equipped for school or manners or piano.  She fought back, challenged her foster-mother's authority at every turn, and when she was punished for this, she fought back twice as hard.



She might have gone insane if it wasn't for Rollo.  She'd stumbled onto the mangy, hostile puppy in an alley between her after-school classes and home.  After earning his trust with scraps of her lunch over the course of days and weeks, she brought him home and chained him up at the very back of the expansive backyard, out of sight of the house.



She had stayed quiet when her foster-mother complained about the neighbor dog's barking, feeling a confused mixture of smugness and terror every time it came up.  Her lunch money went towards buying the dog scraps of food, guessing at what he needed, and this sacrifice of her lunches coupled with the frequent lack of dinner left her getting headaches and her stomach growling constantly during school.  She would wake up at four in the morning to visit him and play with him, and the lack of sleep left her so tired she would drift asleep in the middle of class.



But a dog couldn't be chained to a tree, not for twenty-two hours out of every day.  She'd seen him grow increasingly agitated and unhappy, to the point that she couldn't play with him without him hurting her.  So she'd untied him to take him for a walk.  He'd slipped free and headed for the house.  Her blood running cold, she'd chased after him.



When she caught up to him, she found him in the pool; she couldn't swim, and he couldn't climb out.  She'd pleaded with Rollo to come out of the pool, tried to run around the pool's edge to get to him so she could pull him free, but he'd been scared, and swam away from her.



Then the plastic cover of the pool began to slide closed.  When Rachel had looked to the house, she'd seen her foster-mother standing on the other side of the sliding glass door that opened into the backyard, her finger on the switch.  Slowly, gradually, despite her screams and banging on the locked door, the cover had slid over Rollo's head, trapping him.  For nearly a minute, there was the bulge beneath the cover of Rollo's head as he swam in tight circles, his sounds of distress muffled.



Her foster-mother's punishments always matched the crimes.  There could be no doubt Rachel knew the dog from her pleading and shouts, and having a dog was against the rules.  Or maybe it wasn't even that.  Maybe it was the fact that she was making a disturbance at five in the morning, or the realization that the barking that had plagued her foster mother for so long was Rachel's fault.  Whatever the reason, the dog was to be disposed of, much in the same way as a plate of dinner was thrown out for holding a fork the wrong way or sitting at the table with her legs too far apart.



She'd woken to her power in that moment of panic.  Fed by her power, Rollo had grown enough to tear through the cover.  He'd then torn through her foster mother.  The shrill screaming of her foster siblings indoors had drawn his attention, and he went after them too, pouncing on them like any excitable dog might do with a mouse or rabbit.  He'd torn through door frames and walls, and an entire section of the house and collapsed in on her foster family.  In one fell swoop, she lost the closest things she had to a home and family.  It hadn't been perfect, it had been nightmarish at times, but she'd had so little for so long, she found herself clinging to the scraps she did have.  She ran, then, and she kept running for a long time after that.



Her breath hitched as she drew in a breath.  She shook her head violently, to shake away the tears.  She had stopped screaming, but her dogs were making up for it as their voices had joined hers and continued long after she'd stopped, almost drowning out Angelica's howls.



So many bad memories.  Memories she wished she could purge from herself, scour from her brain with fire and bleach and steel bristled brushes.



She was unhappy because humans were pack animals, she decided.  Taylor and Lisa and Brian could smile and laugh because they had their pack, they had their family members and they had each other.  Alec was more of a loner, but he could still joke and laugh with Brian.  They had their pack, their dynamic.  She wasn't really a part of it.



Bitch knew that she wasn't a lone wolf by choice the way that Alec was.  There was a void there, some part of her that craved that human connection because she was a human and that's what humans needed.  The way things had played out, things she had no control over, she'd never had a chance to figure out how to deal with people, how to invite them in to fill that void.  Friendships and family, conversations and jokes, being close to others and knowing when to speak up and when to stay quiet?  They were treacherous things, littered with complicated nuances, bad associations and worse memories.  Even if she somehow got something right, she always managed to fuck it up sooner than later.  Easier to leave it alone, easier to stay back and not try.  And if they got in her face, if they challenged her and didn't let her keep them at arm's length?  It was easier to fall back on what worked and what she knew than it was to try to guess how to respond.  Violence.  Threats.  It earned her respect, if nothing else.



Then Taylor had made overtures at friendship.  Taylor had invited herself into that place, that void, and had \emph{stayed} when Bitch fucked up.  The scrawny kid had stood her ground instead of running when Bitch called her out on something.  And maybe, just a little, in some small way, Bitch had gotten a glimpse at what she'd been missing out on.



Only to find out it was a ploy.  An act, so that Taylor could get the group's confidence.



And now the others had \emph{forgiven her}?  So easily?  She could see them fawning over the little traitor.  And there was nothing she could do about it.  They liked Taylor \emph{more}.  They would keep Taylor on the team and make Bitch leave if it came down to it.  She knew it in her gut.



So she'd done something stupid.  She'd tried to get rid of her teammate, and she'd done it in a way that haunted her.  More than anything, more than all of the people she'd hurt, the people she'd accidentally killed, or the days she'd scrounged in the trash for food when she'd been homeless, wandering the cities on her own, she hated herself for what she'd done to Taylor.  She had acted like the people who haunted her memories, using what should have been a position of trust to try to hurt someone.



And she didn't know what to do about it.



A gunshot startled her from her thoughts.



``Go!'' she shouted.  ``Go!''



More cracks of gunfire echoed through the night as her pack arrived on the scene.  Angelica was there, her form hulking and rippling with muscle to the point that she couldn't move as fast as she otherwise might.  That was fine.  Angelica couldn't move as fast these days, anyways.  Not since Fog had hurt her.  She was more comfortable like this; she was big, strong and able to move without pain.



Angelica flinched and backed away as the shots came, striking her flesh.



There was another shot, and Bitch saw a flash from the window, a glimpse of a face.  Her face twisted with rage.  ``Attack!''  her voice was shrill.  She leapt off Bentley's back so he could go too.  ``Fetch them!  Fetch!  Go, go!''



As they'd done at the previous location, her dogs tore through the building.  This time, though, they came back with people in their jaws.  Arms, legs and torsos in fanged grips.  Men, women and children.  Some screamed where the dogs didn't know their own strength and bit too hard.



She found the man she'd seen in the window and stalked over to him.



``Fuck, fuck, fuck, fuck,'' the man repeated the word.



``You insulting me?  You trying to act big?''



``What?''  The man's eyes widened.  Was he staring at her, challenging her?  Was it a fear response?  Was he rallying to fight, trying to get a wider sense of his surroundings?  She could only guess.



``No,'' he said, his eyes moving around, as if searching for help.



Defiance?  Sarcasm?  A lie?



``I don't think you realize how badly you fucked yourself.  You.  Shot.  My.  Dog.''  She looked at Angelica.  Her baby wasn't acting too hurt, but he'd \emph{shot} her.  He could have \emph{killed} her, if the bullet landed in just the right place.



She kicked him in the face, and his head rocked back.  Blood fountained from his nose.



``I didn't know,'' he managed, huffing out air, blood spraying at his words, where it had run down to his lips.  ``Didn't know she was yours.  She was scary, I- I reacted.''



Was he lying?  She couldn't tell.  She'd grown up with so many good liars, it felt like everything that sounded honest was a lie.  If he \emph{was} lying, and it was obvious, she'd look weak if she fell for it.  Others might not get the message about this being her territory, about her dogs being off-limits.  If he wasn't lying\ldots well, he'd still shot Angelica.



``\emph{Nobody} hurts my dogs.''



``Please.  I have a wife, kids.''



As if \emph{family} somehow made you better than someone else?  The idea nettled Bitch.  Life experience had taught her that it was all too often the opposite.  People were assholes, people were monsters.  The exceptions were all too rare.  Far too many of those same people started a family just because they thought it was what they should do, and then they were assholes and monsters to a captive audience.



She kicked him again, in the stomach.  He screamed as the kick made his arm, still in Ink's jaws, wrench the wrong way.



``Angelica,'' she ordered.  She kicked him in the stomach again.  ``Paw!''



Angelica stepped forward and placed one paw the breadth of a truck tire down on the man's pelvis.  He howled in agony, his words rapid, desperate and breathless, ``Heavy oh god please stop please let me go make it move itscrushingme!''



She looked at him with distaste.  It bothered her that the only time she could be absolutely sure what someone meant, what someone wanted, was in circumstances like this.



``Angelica,'' she ordered, ducking beneath Angelica's outstretched limb, kicking him in the kneecap, ``Take it.''



Angelica bent and gripped the man's legs in her teeth, twisting his body further.  His body was pressed to the ground by her paw, his arm and legs pulled up and away from it.



She stepped close to Angelica, burying her face in the slick muscle and hard tissues that layered the dog, wrapping her arms as far as they would go around Angelica's shoulders and neck.  Just as her dogs came to trust her as she cared for them, fed them, and nurtured them, she grew closer to them as they shared experiences with her, as they learned and accepted their training.  Angelica was one of the dogs she was closest to.  The \emph{only} dog she was this close to.  Brutus and Judas had passed, the only dogs she had been with for \emph{years}.



Her heart broke a little every time she thought about it.



And this man?  This \emph{family} man?  He'd thought he could take Angelica away from her?



Without looking at him, her head still pressed to Angelica's neck, she gave the order, ``Hurt him.''



She felt the vibration rattle through Angelica's head and neck as bone snapped and crunched between her teeth.  The man shrieked, there was no better word for it, and others in the vicinity echoed his shrieks with their own.



She gave the hand signal and an order, ``Drop him.  Dogs, drop them!''



Angelica let the man drop.  His shins were cracked, the ends of his legs bent at odd angles.  One by one, the other captives were dropped to the ground.  Each of the man's noises of pain was a little smaller and quicker than the last.



``Why can't you fuckers get it through your skulls?'' she called out.  ``This is \emph{my} territory!''



``We didn't know,'' someone said.  A woman who was clutching a bloody arm to her chest. Her daughter beside her.



``You fucking challenging me on this?''



``No!  No.  We- we just\ldots how were we supposed to know?''



``Are you retarded or something?  It's obvious,'' Bitch couldn't believe the woman's stupidity.



``How were we supposed to know!?'' the woman raised her voice, sounding plaintive.



``The howling.  If you can hear the howling, you're too fucking close.  \emph{Leave}.''



``You could probably hear that halfway across the city!''



``No fucking shit,'' Bitch retorted.  The woman was challenging her authority.  She had to respond to it, or the woman would keep talking, Bitch would say or do something that made her look stupid, and others would stand up to her.  Best to stop that sooner than later.  ``Socks!  Come!''



The woman shrank back, clutching her daughter, as Socks advanced to Bitch's side.



``Stop,'' a voice ordered.



Bitch turned and saw two capes.  From New Wave, weren't they?  Brandish and Glory Girl.



Brandish spoke, ``Glory Girl, call your sister.  At least one of those people needs medical attention, fas--''



She stopped as Bitch whistled as hard as she could.  Barking and snarling, her massed dogs charged the heroes.



After being ambushed and taken captive by the ABB, she'd learned her lesson.  Hit first, assess the situation later.  Besides, what was she going to do?  \emph{Talk} to them?



Brandish flicked her hands out, and beams of light drew into vague sword shapes.  As the dogs stampeded towards her she flicked them out to double the length.  They drew closer, almost reaching her, and she reconsidered, banishing the weapons to condense herself into a beachball-sized ball of orange-yellow light. The dogs hit her, there was a spray of sparks, and the ball was sent careening down the street and through the wall of a building.



Glory Girl was flying over the stampeding dogs, a cell phone pressed to her ear, in Bitch's general direction.  Ink and Bruno leaped to the side of a building and then leaped from that point toward Glory Girl.  She struck Socks across the head, sending him flying to the ground, and Bruno slammed into her, knocking the phone from her grip.  She brought her knee up into the dog's side and pushed herself away before he could drive her down into the ground.



The heroine went for Bitch, who had only Angelica at her side.  Angelica positioned herself between enemy and master, and Glory Girl hit the dog broadside.  Angelica barely reacted, turning instead to snap at Glory Girl.  Her teeth rebounded off the heroine's outstretched arm, and Glory Girl darted backward, to hover in the air.  Catching her breath?  Watching the situation?



That wasn't how you were supposed to fight.  Bitch whistled hard, then shouted, ``Magic, Lucy, Roxy!  Come!''



As the three dogs barreled toward her, she used her power.  She felt it extend outward like a vibration from deep inside her.  She felt that power shudder and reverberate, as if to let her know it was making contact with them.  She could see the effect.  Could see them grow larger, see bone and muscle swell and shift.



``Attack!''



In moments, Glory Girl was contending with four dogs.  Angelica advanced implacably, Bitch following at a walking pace.  The other three were attacking from every direction, cutting off escape routes, leaping onto the side of the building, leaping down, running behind her, or flanking her from the sides.



``Mom!'' Glory Girl shouted, a note of panic in her voice.



``Run!'' Brandish called out her response.  She was facing much the same situation, unable to attack with the relentless pressure the dogs were putting on her.  Instead, she changed herself into that ball form where she couldn't be touched or hurt, flying away with every hit she took, or controlling the direction so she could make her way for an escape route.  She managed to find enough pause to lash out at one dog and shout, ``Get the wounded!''



Glory Girl caught Roxy around the snout as the dog lunged for her, and threw her down at Lucy.  She used the momentary reprieve this granted her to fly straight for the man who'd shot at Angelica, who lay in a heap on the ground.



She stopped mid-flight.



A woman stood over the man's mangled body, her long hair blowing slightly in the wind.  Which seemed wrong.  With the light rain, her hair should have been wetter.



Glory Girl looked over her shoulder to see the dogs, looked back to the injured man and the woman, and then flew straight up, disappearing into the gloom of the night sky.  She'd left him behind.



The barking and snarling ceased as the fight drew to a close.  Each of the dogs returned, and Bitch noted a few injuries.  A shattered plate of bone here, a gouge where Brandish's blades had made contact there.  Surface damage.  It was only the damage that penetrated deep, past the layers her power applied, which risked hurting the dogs or doing permanent damage.  Nothing so serious.  Bitch breathed a sigh of relief.



She stalked forward, her dogs joining her to form a loose circle around the woman.  The crazy bitch was naked from head to toe, and her skin and hair were painted in alternating stripes of white and black, like a zebra\ldots no.  Paint would have washed off, and dye wouldn't be so crisp around the edges.  It was a natural coloring.



When the woman looked up at Bitch, her eyes were yellow and bright, reflecting the ambient light like the eyes of a dog or cat might.  She smiled, and there wasn't a trace of tension in her body, as though she'd just woken up in a safe place.



``Who the fuck are you?''



The woman didn't reply.  She crouched down beside the man, then shifted her position so she was sitting sideways, her legs stretched out beside her.  Her fingertips traced the man's injuries, almost lovingly.



``Answer me,'' Bitch ordered.



The woman reached over and pressed her index and middle fingers to the man's eyes.  Pressing down, she penetrated the orbs, sliding her fingers down until they were two knuckles deep.



``Hey!  Fuck off!''



The woman removed the fingers.  Vitreous fluids and blood flowed from the open wounds in the man's eye sockets.



The woman turned towards her.  She didn't meet Bitch's eyes, instead looking down at Bitch's feet.  It struck Bitch that the woman was making herself small, was being inoffensive.  It made her feel better, strangely.



Slightly calmer, her words measured, she called out, ``I'm going to ask you again.  Who the fuck are you?''



``Siberian,'' the woman spoke, her voice barely above a whisper.  Barely audible.



``What the hell are you doing here?  This is my territory.''



``I'll leave soon.  I just wanted to talk.''  Again, the whisper.



\emph{Talking, always talking.}  ``Not interested.  Go.''



Siberian looked down at the man, who was still writhing and twitching, making small noises of pain.



``Go!''  She shouted.  The woman didn't budge.  Bitch glanced at her dogs to see who was the biggest, the least injured.  Lucy.  ``Lucy!  Attack!''



Lucy pounced on Siberian.  Bitch saw Siberian stretch out her arm, saw Lucy's jaws clamp down on the limb.



There was no reaction.  Lucy tugged, the full force of her body behind the movement, and the woman didn't move a hair.



With great care, Siberian stood.  She looked at Lucy, her bright eyes roving over the dog's face and the length of the dog's body.



``Beautiful,'' she whispered.  She pressed her lips against Lucy's nose in a kiss, as if uncaring that the dog had seized her arm between jaws that could crush a motorcycle.  Lucy snorted in response.



Then she looked at Bitch.  This time, she made eye contact, and despite her whisper, there was no-nonsense in her tone.  ``Your dog lets go of me now, or she gets hurt.''



The confidence in the tone, the authority, the fact that the woman's eyes didn't waver in the slightest, they made it abundantly clear to Bitch that the woman was telling the truth.  She was certain enough about it that it was worth weakening her position here.  ``Lucy, off.  Come.''



Lucy let go and backed off, moving to Bitch's side.



``They're beautiful,'' Siberian whispered, looking at the dogs.



Bitch nodded mutely in response.



Siberian approached her, walking with a great deal of care.  There was grace in her movement, and she walked on her tiptoes, each foot carefully placed a measured distance in front of the other.  Her eyes shone through the curtain of her white and black hair.



Bitch felt a moment's trepidation.



``What\ldots'' She regretted opening her mouth the instant she did, but it was already too late.  ``do you want?''



``\emph{You}.''



``I don't understand,'' she tried to inject more confidence into her answer.



``They told me I should pick someone.  Someone they can test.  I read about you, I heard about you.  I want you on our team.''



``Team?''  She hated the short answers that were coming out of her mouth, the way that they were uncertain and they put her on weaker footing.



The woman's response carried over the flooded street, through the growls that slowly ratcheted up from the dogs as the stranger approached their owner, ``The Nine.  We have only eight, not enough.  So some of us are picking people.  Then we test them.  I picked you, and I \emph{like} what I've seen.  I've been watching you for weeks, now.''  She smiled again.



\emph{Has to be a lie}, Bitch thought.  Her dogs would have noticed someone following her, wouldn't they?



The woman was only a few paces away.  The question was, should Bitch retreat and put herself in an even weaker position, or did she stand her ground?



She stood her ground.  The woman stepped closer, within arm's reach, then another two paces, until her chest pressed against Bitch's body.  She met the woman's gaze, unflinching, until Siberian wrapped her arms around her, holding her close, resting her chin on Bitch's shoulder.



``Aren't you tired of pretending?'', the woman whispered in her ear.



``What?''  Bitch tried to pull away, so she could ask the woman the question to her face, but the limbs were unmoving, more resisting than steel bars would have been.



``Acting like one of them.  Playing and losing their games, decorating yourself in their clothing and their symbols, following their rules?''



``I--'' Bitch paused, ``Don't know what you're talking about.''



The pause was telling.  She \emph{knew} it was telling.  The woman understood her, she knew.



\emph{The woman understood her}.  The thought clicked.  The way the woman moved, her body language, everything, she was making sense to Bitch in a way that so few people did.



The idea left Bitch shaken.  How?  Why?  Was it some power?  From the start, she'd known what the woman wanted to express as easily as she did with her dogs.



``You're an animal, \emph{Bitch}.'' The woman gave special treatment to that last word.  Bitch stiffened.  The woman pulled away, one hand remaining to caress the side of Bitch's face.  Her eyes were lowered again, Bitch noted.  She was smiling lightly, her lips pressed together, teeth hidden.  Playful, gentle.  Bitch let herself relax.  It hadn't been meant as an insult.  The body contact was intrusive, but she could grit her teeth and bear it, at least until she figured out who this person was and how she could fight back.



``We're all animals,'' Siberian murmured.  She walked over to Bentley, and Bitch hurried to give the dog the hand gesture for `stay', then `off' before the woman moved to touch him.  ``Some more than others.  \emph{You and I}, more than others.''



``Philosophy shit?''



Siberian smiled, her hands tracing Bentley's snout, the exposed muscles and horns.  ``Philosophy shit.  Yes.  \emph{Touch\'{e}}.  An idea given meaning because people think it should have meaning.  But it's just words, isn't it?''



``Sure.''



``Join me.  Stop pretending to be like them.  You know you're bad at it.''



``I'm fine where I am.''



``Mmm,'' the woman smiled, her eyes lowered.  She clasped her hands together and pressed them to her chin, squishing her breasts up against her chest.  She turned, taking in the neighborhood, assessing Bitch's territory.  ``Maybe for now.  You have freedom to run, to do as you like.  It's nice.  But you're going to chafe at it sooner or later.  You're going to realize that you're still in a cage \emph{they} made.  You're still following their rules, in the end.''



Bitch looked around the empty, flooded streets as Siberian was doing.  She didn't answer.



``Maybe you can be happy like this.  A dog, collar around your neck, a fenced in territory.  You'll never \emph{really} understand what they're all talking about.  The best you can hope for is a pat on the head when you're good, when you do as you should, maybe some companionship whenever you're a \emph{good girl}. But maybe that's what you want.''



``As opposed to what?''



``Being wild.  Being free.  \emph{Truly} free.  It's \emph{exhilarating,}'' Siberian breathed.



Bitch frowned.  Words that sounded nice, but that was all they were.  Just words.



``I'm going to give you two presents, \emph{Bitch},'' Siberian whispered.  ``One will be waiting for you when you go back to your\ldots what do you call it?''



Bitch didn't answer.



``Let's call it your \emph{den}.  I like that.''



Siberian closed the distance to Bitch with a surprising speed, her steps less controlled, carrying her long distances forward as she zig-zagged over the flooded street.  Before Bitch could react, or before the dogs could step in, she was next to Bitch, stopping.  Siberian put a hand on her collarbone.  Bitch was lifted into the air and pushed down into the water, soaked, landing hard enough that the air was forced out of her lungs.



As she struggled to breathe, Siberian whispered, ``The second gift is \emph{special}, a treasure for a kindred spirit.''



Bitch coughed, struggled, but she couldn't move the hand.



``As of this moment, you're the only one to hear me speak and live afterwards.''



She kissed Bitch on the forehead, like a mother would with a child.  Bitch tried to twist away, and only succeeded in getting water in her eyes and nose.  She sputtered as she struggled to draw air into her empty lungs.



When she could see again, Siberian was gone.  Her dogs were looking up at a nearby rooftop.



Shaken, she gestured for Bentley to come to her, and climbed up onto his shoulders.



Coughing, snorting water from her nostrils, she gave the order, ``Home.''



Her thoughts were chaotic as she rode Bentley down the streets, a dull roar of too many things all at once, all too important to be ignored.  At the same time, she didn't want to think about them, didn't want to put those pieces together, because she wasn't sure she liked where they would lead.



The gift Siberian left her.  Some of her henchmen were at her den.  More important, some of her \emph{dogs} were there.  Every minute the trip took left her more worried.



She hopped off Bentley as they arrived at the building, shoving the doors open.



Blood.  Trails leading to Barker and Biter, who were on the ground floor, unconscious, still breathing.  One of the girls, the one with veterinary training that Coil had sent to her, was sitting in one corner, nursing an arm that dangled at the wrong angle from the elbow, sobbing.



This was recent.  Siberian had done this in the time it took Bitch to get here.



More blood, one of the boys, a dog groomer with years of experience, lying beside the kitchen counter, his shirt wadded up and pressed to his face.  Around the shirt, she could see the four parallel tracks where Siberian's fingernails had left gouges running across his face.



None of the dogs were hurt.  She had to double-check them to see.  Most were cowering in the corners.  Some had retreated up the stairs.



The blood had a pattern to it, as though Siberian had painted a picture with the spray.  A line drawing from each of the injured to the center of the room, where a box sat, faintly dusted with flecks of blood.



She was nervous as she opened it, but she couldn't \emph{not}.



A furry bundle tried to escape, and she stopped it.  It bit for her fingers.  She pulled her hand back, gripped it by the throat and forced it down to the ground, making her dominance clear.



A husky puppy?  No.  The physical makeup was wrong.  The smaller ears, longer limbs, and markings around the jowls and muzzle.



A \emph{wolf} pup. Where had Siberian found this?



There was a card in the bottom of the box, stained with urine.  Bitch picked it up with the very tip of her finger and thumb.  She'd never properly learned how to read, so she had to work out the individual sounds, moving her lips to try to piece it together.



``Ah\ldots air yoh\ldots you.  Air you a\ldots''  That letter, she didn't recognize it.  After it was\ldots ``oll\ldots wolf.''



She gave up.  She could guess, anyways.



\emph{Are you a wolf, or are you a dog?}



The rule was to call Coil at a time like this.  To let him know what had happened.  She found her phone in one of her jacket pockets and she fumbled with the keypad to find him in her contacts.  Her finger hovered over the button.



What was she holding on to?  Who was she protecting?  Her friends?  Were they really her friends?  It wasn't that she wanted to betray them, she wasn't about to repeat that mistake, but\ldots



She couldn't articulate the thought, but it was Taylor's face that flashed into her mind's eye when she put the phone away.



Maybe she would see what this test was about.  She wasn't about to back down.  But in the end, \emph{she}`d make the call about where she went and what she did.



``You,'' she told the man with the gouges in his face, ``Go to a doctor.  Take anyone here that needs it.  But I don't want you telling Coil, I don't want you using \emph{his} doctors.  Got it?''



The man looked up at her, staring for long seconds.  Finally, he nodded.  She didn't know if he would, or if he'd be able to hide it, but if he did inform Coil, it would at least be an excuse to get rid of him and the others.



She looked down at the wolf pup, who was still struggling to bite at her fingers.  She let it go, waited until it tried to attack her again, and pushed it down onto its side once more.



``Little bastard,'' she smiled.



Almost without thinking about it, she used her power.  Just the smallest amount.  She felt almost none of the vibrations or shudder she experienced as a visceral feedback on her power with the other dogs.  It was only when she saw his skin splitting that she realized it was actually working.  Faster, quicker, with so little of the temporary exhaustion she so often experienced on her end.



Was it \emph{easier} with him?  What did that mean?





