





Theo clutched the remote control in both hands.  For five minutes, he hadn't taken his eyes off the TV set.



For those same five minutes, the TV set had been off.



``Who's a pretty baby?  Who's a pretty little girl?  You are! Yes you are!''



Aster squawked in one of the little cries that foretold an incoming tantrum.  Theo clutched the remote control tighter.  He felt a throbbing pain where the corners of the remote bit into the heels of his hands.



``Oh, don't cry, don't cry!''



Theo's throat was dry, every thud of his heartbeat seemed to make his hands shake and his vision waver.  He'd never been more intimately familiar with the television itself.  The shape and color of the TV set, the proportion of the screen to the outer frame, the little border of silver around the very edges, and the `Starry' brand name logo at the very bottom.  He suspected it would be ingrained in his memory for the rest of his life.



Which might just be a very short span of time.



``Nope.  Don't see the appeal.  Hey, boy.''



Theo's heart leaped in his chest.  He tore his eyes from the television and looked up at the man who was cradling Aster.



``The baby needs to be changed.''



Theo nodded and stood.  He was reaching for Aster when the man threw the baby at him.  He had to scramble to catch her, almost let her slip through his arms, and only just barely caught her by pressing her against his stomach and pelvis.  She started screaming.



``Don't drop her, now, or I'll be \emph{very} annoyed.''



Theo nodded, raising his voice to be heard over Aster's shrieks, ``Yes sir.''



``Must you keep calling me that?  Do I really look like a sir?''



Theo looked at the thirty-something man.  He wore a dress shirt that was open to show his muscled chest and stomach, and had the sleeves rolled up to expose his forearms.  His tight jeans were low slung, his limbs long, and his hair was longer and greasy.



The man's beard had been trimmed, but scruff was growing in around the edges, obscuring the intricate pattern that had been trimmed into the inside border of the  facial hair.  A knife danced around his fingers constantly, making Theo flinch every time the blade turned to point toward him and Aster.



Jack Slash.



``My father told me I should address my betters as sir, sir.''



Jack laughed with the slightest touch of derision.  ``Well, your daddy taught you well, didn't he?''



True enough.  Theo wondered if this measure of respect played any part in why Jack had let him live this long.  ``Yes, sir.  I'm going to go change the baby.''



``Yes.  Do.''



Theo's hands shook as he adjusted his grip on Aster, hauling her up until her head was at his shoulder, even though that meant she was screaming in his ear.  He carried her to the changing table and set her down.



Kayden had reclaimed her old apartment after the catastrophe, found many of her possessions still there.  The man never let the front door out of his sight as he walked around the living room, and was soon behind Theo.  With the open window, Theo could hope the man was upwind of the aromatic diaper.  How long before the squealing of the baby, an offensive smell or something else set the psychopath off?



``How long until your mother gets back?''



That was something else.  That was the third time Jack had asked the question.  Was his captor's patience running out?



``She's not my mother,'' Theo changed the topic.  He dropped Aster's dirty diaper into the bin.



Jack walked up to Theo, until he was just behind the boy, his shadow cast long by the setting sun, stretching over Theo and the changing table.  Theo could feel the tension ratcheting up.  ``I'm going to get upset if you lie to me.''



Theo didn't take his eyes off the baby, forced his fingers to keep working on the diaper.  ``Kayden is Aster's mother, sir, my dad's ex-wife.  She's been taking care of me since my father died.''



``Of course, of course, now I understand.  I believe you,'' Jack said, before chuckling.  He turned and walked away, leaving Theo breathing out a shuddering sigh of relief.  When Jack spoke again, there was no humor in his tone.  ``Do you love her?  The mother of that baby?''



``Yes, sir.''  \emph{But I don't like her}.



``Good, good.  Does she love you?''



``No sir.  But she likes me.''



``Ohhhh?'' Jack drew out the sound, and it was vaguely mocking.  ``Do tell.''



``I- I take care of Aster for her.  I do my chores, I don't talk back.  I don't make life harder for her,'' Theo began.  He swallowed, ``But my dad treated her badly, and I think she sees him when she looks at me, and she'll never let herself love me because of that.''  \emph{She has to look past the doughy face to see Dad in me, past the baby fat I never seemed to lose, but I have his genes, I look like him, beneath it all}.



``\emph{Do} you have some of your father in you?''



Did he?  ``I'd like to think not, sir.''



``I'm remembering now.  Kaiser.  His name in costume was Kaiser.  I met him once, don't you know?''



``I didn't know.''



``Years ago.  Allfather still ruled Empire Eighty-Eight then.  They held a big meeting between all of the factions.  We stopped by.  Great fun.  I don't think they accomplished a thing that day.  We provoked a bidding war instead.  Group called the Teeth wound up hiring us to kill some members of the Protectorate team.  We did it, and then we wiped out the Teeth before leaving the city.''



The Slaughterhouse Nine must have been new, then.  People today would know better.  Hopefully.



Jack chuckled lightly, ``I digress.  I do remember your father.  He was older than you are now when I saw him.  He talked in a way that made me think he was an athlete.''



``He was, sir,'' Theo confirmed.  \emph{And he was disappointed I never followed in his footsteps.}



``There were more teams in this city, then, more villains.  Not many heroes.  Lots of scary motherfuckers around, and yet I could probably count on one hand the people who made eye contact with me.  Even then, when my reputation was a fraction of what it is today.  Your father was one of those people.  Ballsy fucker.''



``Maybe he thought you'd respect him for it, sir?  He was always good at reading people.''  \emph{And making them do what he wanted}.  \emph{Even me}.



``Is that so?  I'd like to think I'm much the same.  A people reader.  But \emph{my} interest is in the design of people. What makes them tick?  What holds them together?  All too often, it's one little thing.  In architecture they call it a keystone.  The one stone that keeps the entire arch from collapsing.  The weak point.  And I'm very, \emph{very} good at finding those weak points.  Can you guess what I'm talking about here?  Why I'm in this apartment?''



``Aster, sir?''



``And you say you're nothing like your father.  You're sharp, little boy.''  Theo couldn't see Jack move, but again, the man's shadow fell over him.  He felt himself shrink down, as if the shadow weighed on him.



``Thank you, sir,'' he managed.



``Yes.  See, my compatriots are all busy with a task, tonight, you understand.  I bet on the wrong horse.  Come.''



Jack's hand fell on Theo's shoulder, and he flinched.  Still, he scooped Aster up and followed as Jack led him to the front of the apartment.  There was a trail of blood leading from the front door to the nearby bathroom.  Jack gave Theo a push on the shoulder, but remained outside the bathroom, where he could watch the front door.  Theo entered.



There was a man in the bathtub.  He'd seen Jack drag the man inside, had heard the taps running.  What he hadn't expected was for the man to be alive.



The bathwater was crimson, and the man lay in a sea of things that had been taken from the freezer and dropped within.  He was Japanese, Theo noted, his hair cut short, his body bearing the lean muscle of someone who'd honed their body into a weapon, and he was unconscious, though breathing.



``Oni Lee,'' Jack spoke from outside the bathroom.  ``Our habit is to nominate a certain individual.  Then the others test them in their own ways.  If that individual passes the test, they are recruited to the Slaughterhouse Nine.''



Theo didn't know how to respond, so he kept his mouth shut.  He rocked Aster in his arms, using one hand to shield her eyes from the scene.  Not that he thought she could make it out or understand what she was looking at, but it made \emph{him} feel better.



``I had a little conversation with Oni Lee.  Found him living above a grocer's, with the help of one of my teammates.  Someone shot out his kneecap, it seems, and he's been restless ever since.  A few kills here and there, but perhaps a little harder when you can't walk.  Need the right time, the right place.  I kind of respected that, and the fact that he was another fan of knives was a point in my book.''



``Yes, sir.''



``But we didn't even make it to the test.  I told him we had tinkers that could fix him up.  He was interested.  Then I told him he'd have to prove himself, he asked me how.  Now, it isn't always done, that a member of the Nine tests their own candidates, but I decided to anyways.  Something off about him, wanted to make sure he didn't embarass me.  Told him to come up with something, and he couldn't.  Do you know what \emph{tabula rasa} is, boy?''



``No, sir.''



``Blank slate.  A piece of paper with nothing on it.  A formatted computer.  A tombstone without the name on it.  Seems that fellow can copy his body just fine when he teleports, but something in his mind gets left behind.  Once I realized it, picked up on the fact that he was little more than a robot wanting his orders, I informed him I had decided we had no need for his services, we fought, and\ldots here we are.''



``I see.''  \emph{And Jack was in one piece, while Oni Lee was bleeding out into the bathtub.}



``So.  Come on out of the bathroom, now.'' Jack ushered Theo out of the bathroom with the dying man. ``There we go.  Back to  the subject of Purity and the baby\ldots  Aster?''



``Yes, Aster, sir.''



``We're going to play a little game.  See, the moment Purity steps in that front door, I give her just a moment to take in the scene\ldots and then snicker-snack, you and the baby die.''



Theo felt his blood run cold.  Tears appeared in the corners of his eyes.  \emph{I'm going to die}.



``I'll get to savor the expression on her face as she watches her keystone crumble.  I'll get to see how she responds as that element in her life that supports everything else bleeds out on this nice white carpet.  Maybe say something to just \emph{twist the knife}.'' Jack mimed a lunging stab and then slow turn of his blade.



Straightening, Jack looked Theo over, ``A pity she doesn't love you, but if she likes you, at least, then it'll have to do.''



\emph{Why did I tell him that?}



``She'll kill you, sir.''  Theo said.  Then he added a hurried, ``No offense.''



Jack waved him off.  ``She'll try.  So many have, and they've all failed so far.  But it's good that it's a little dangerous, a little risky.  It's no fun if I know how it's going to play out.  Some unpredictability, it gives spice to life.  Maybe I'll kill her right after I see the look on her face.  Maybe I'll escape and leave her to wallow in her misery.''



\emph{Escape?  From a fifteen story apartment building, against a supervillain who can fly and level city blocks?}



Then again, Jack had done worse things than murder the child of a cape like Purity, and he was still here.



``Sometimes,'' Jack started, pausing as if he was constructing the thought as he spoke it, ``I like to imagine the impact I've made on the world.  What possible realities am I pruning, what events am I setting in motion, each time I take a life?  If the flap of a butterfly's wing can alter the course of a hurricane, what am I doing when I take a human life?  The life of a person who interacts with dozens of people every day, who would have a career, romance, children?''



Tears ran down Theo's face.  He clutched Aster tight.



``Can you tell me who you are, Kaiser's boy?  What am I doing to reality when I open you up from cock to chin and let your entrails spill onto the floor?''



``I-I don't know,'' Theo said, his voice quiet.



``Don't shut down on me, now.  Here, I'll make you a deal.  If you give me a good answer, I'll make it quick.  Thrust my knife right through the center of your brain.  It'll be like flicking a light switch.  You just stop, and there'll be no pain.  It'll be as dignified as death can be.''



``I--''  Theo shook his head.



``I'll even let you relieve yourself in the bathroom beforehand so you don't shit yourself so badly when you drop dead.  You'd have to be quick, unless you want to be on the toilet when she comes in, but it's a chance few get.''



``I wanted to be a superhero,'' Theo blurted.



Jack laughed abruptly enough that Aster was spooked and started screaming louder.  His laughs continued for several long seconds.



Theo went on, as if Jack were still listening, ``I'm probably going to get powers, because I'm Kaiser's son.  But I don't want to be a member of Purity's group, I don't want to cleanse the world or try to fix things by killing or through hate.  Sir.''



``And you'd fight people like me, I suppose?''



Theo nodded.



Jack was still grinning.  ``What would you do to people like me, then?  Let's say you got powers.  Would you right wrongs, lecture schoolchildren on doing what's right, and see bad guys like me carted off to the Birdcage?''



Somehow, knowing the inevitability of his own death gave him a measure of courage he had never had before.  Even so, it took all of the willpower he had.  Theo met Jack's eyes for the first time.  The man's eyes were a very pale blue, and there were lines at the corners.



Theo swallowed the lump in his throat.  ``People like you?  I'd kill.  Sir.''



Jack broke into a second spell of hysterical laughter, and it was all Theo could do to keep Aster from squirming out of his grasp in her distress.



``Can't--'' Jack had to break off to let another small laugh pass, ``Can't say I can imagine that, boy.  You, as one of the vigilantes?''



\emph{Neither can I}, Theo thought, but he remained silent.



``But you've piqued my interest, and if there's any reason I do what I do, it's because I find it \emph{interesting}.''



Theo could see the cell phone on the coffee table in the living room light up and shift position as it vibrated.  It happened behind Jack, and the man didn't appear to see or hear it.  The only person who called Theo's phone was Kayden, and she'd been out getting groceries.  It was routine for her to call for him to open the lobby door, then come down to help bringing them up from the lobby\ldots



She was coming up.  He was almost positive.  Could he distract Jack and give Kayden the opportunity to put the man down?



``I've changed my mind,'' Jack said.



Theo stared, trying to fathom what the man was saying.



``Don't let it be said that I can't delay my gratification.  Listen carefully now, I'm making you a deal.''



Theo nodded, mute.



``I want to see this.  This picture you paint.  So I'm going to give you a chance to make this happen.''



Theo nodded slowly, but his thoughts were on Kayden's approach.  How long until Kayden opened the door?  Would Jack attack her?  Attack Aster?  Despite what he was saying now?  Or would Kayden attack him and provoke something?



``How old are you?  Fourteen? Fifteen?''



``Fifteen, sir,'' Theo said.  \emph{Hurry up, finish before she comes.}



``Two years then.  Two years to get your powers, to train, to do whatever it takes to become the motherfucking badass you describe.  That should be long enough without risking that one of us gets offed by bad luck or picking the wrong fight.  At that two-year mark?  You hunt me down, you kill, disable or sneak past my Nine, whoever they are two years from now, you look me in the eyes, and then you try to kill me.  If you fail?  If you cannot find me?  If you chicken out?  Hmmm\ldots what's a good consequence?''



In his hurry to resolve this before the door opened, Theo made the first suggestion that came to mind, ``You kill me.''



``That goes without saying.  No.  It should be meaningful.  What's your name, boy?''



``Theo.''



``Fifteen year old Theo.  How many people's lives will you touch in these coming two years, because I've spared your life?  Two hundred?  Five hundred?  A thousand?  How far will the flaps of your butterfly wings extend?''



Theo glanced at the phone.  It glowed and moved again.  Was Kayden in the lobby?



Jack went on.  ``If you fail in this, I'll kill nine hundred and ninety-nine people in your name.  I'll even break my usual rules to get the body count that high, so it's something \emph{special, }beyond my usual habits.  Maybe a bomb, maybe poison.  I'll come up with something.  I can target the people you love, those you're closest to, people you've affected.  Aster there can be the nine hundred and ninety ninth, and you'll be the thousandth.  Perfect.  Canceling out the impact you've made in the world, it's poetic.''



Theo swallowed.  \emph{A thousand people?  }Could he say no?  Could he refuse the offer?  Or would Jack carry what he threatened regardless?



``Well,'' Jack spoke, smiling.  ``I'll be off.''



He stepped into the bathroom, turning away from the door for the second time in his entire `visit'.  When he emerged from the bathroom, he held the naked form of Oni Lee over one shoulder, a knife in his free hand.



``A treat for a teammate, this is,'' Jack winked.  ``Doesn't need to be alive.  Just fresh.  Would you get the door, Theo?''



Theo hurried forward to open the door, shifting Aster in his arms to open it.



Kayden stood on the other side, groceries in hand.



Stern, she said, ``Theo!  I called you twice.  Can you go down to the lobby and get the last two bags of groc--''



She fell silent as the door opened wider, revealing Jack.  In a moment, the bags in her arms were tumbling to the ground, and her hair, eyes, and hands were glowing with blinding light.



``Kayden,'' Theo had to control his voice to keep it from shaking, ``Let him go.''



``I had a wonderful conversation with young Theo here,'' Jack spoke.  He rested his hand on top of Theo's head.  Theo could feel the hard handle of the knife tap against his scalp.  ``Very \emph{interesting}.''



``What are you--'' Kayden started, her voice rising with anger, but Theo lunged forward, gripping her shirt and shaking his head.  She looked down, confused.



Jack waggled a finger at her, ``Don't bother, Purity.  See, I've been studying you.  I go into every possible fight armed with knowledge.  You have a weakness.  A flaw in that power of yours.''



Theo could see Kayden tense, but she obliged when he pushed her away from the door and towards the end of the hallway furthest from the stairwell, stepping back.



``While reading up on you, I tried to put the newspaper clippings and online information in chronological order, and a funny thing happened.  Seems like your power is weaker some days, stronger on others.  I mapped it out.  You have some form of internal battery or fuel that drives your power.  After going days without using your power, you're \emph{stronger}.  After periods where there's more sunlight, your power is stronger.  You absorb light of any kind, I suppose, and later spend it to use your abilities.''



Theo thought he might have seen a tiny flash of concern on Kayden's face.



``It's been an overcast week, and you've been using your powers a great deal, trying to put the Pure on the map.  So think very hard about what you want to do next.  Because if I'm right, and your power is spent, you might not succeed in killing me.  And I would retaliate by killing all three of you.''



``You're underestimating me,'' Kayden spoke, her voice hard.



``Then blast me away.  Turn me into a smear in your hallway, if you think you're strong enough, quicker with your light than I am with a knife.  Prove me wrong,'' Jack smiled.  He waited a few seconds, and the only noises in the hallway were Aster's mewling complaints.



Jack stepped into the hallway and turned toward the stairwell.  ``Thought so.  Be grateful.  That boy is the only reason you and your daughter are alive right now.  He'll explain.  Train him.  Make him strong, make him \emph{vicious}.  Let him take whatever path he needs to take.  You and your daughter owe him that.''



Kayden looked down at Theo, who glanced at Jack for just a second, then looked up at her and nodded quickly.  Urging her.  \emph{Jack wouldn't be doing this if he didn't think he could get away}.



``Alright,'' she spoke.



Jack didn't offer anything further.  His knife twirling in his fingers, he stepped toward the door by the elevators, kicked it open, and stepped inside.  As he made his way down, he whistled a merry tune, the sound echoing through the stairwell until the moment the doors shut.



Theo handed Aster to her mother.  He felt dazed at the magnitude of what faced him.  \emph{Two years}.





