





Spitfire had often complained that having a power based around creating flame meant you faced two kinds of opponents.  There were the people who burned, who were the majority.  Civilians fell into this category.  Unless the person with the power was amoral, which Spitfire wasn't, this actually wound up being a detriment, because of the easy possibility of life altering injuries, death and scars.  The kind of thing that brought heroes down on the villain's head in full force.  The second group was the foes who didn't burn.  People in armored suits with enough covering, people with forcefields, people with foreign materials either forming or surrounding their bodies, the list wound up being fairly long.



``Spitfire, run!''  Faultline ordered.



Burnscar wore a red dress and had chosen to go barefoot rather than wear shoes.  Her dark brown hair was a tangled mess above staring green eyes.  Her skin was pale, giving a greater contrast to the red of her clothing and the dark the circles under her eyes.  The round scars of what were likely cigarette burns formed individual rows down from the bottom of each eye to her jaw.  She strode forward through the flames she'd set on the streets outside Faultline's now-deserted nightclub, Palanquin.  Sweeping her arms to either side, she spread the flames along the breadth of the road, drew the heat into her palms, and then hurled it at her opponents.



Burnscar didn't seem to have the same reservations about incinerating more vulnerable enemies that Spitfire did.



Gregor the Snail caught one fireball with a hurled glob of slime, extinguishing it.  The other landed in the middle of the group, not striking anyone, but nonetheless driving them apart.  Newter was at one side of the resulting blaze in the middle of the street, Faultline and Shamrock at the other, with Gregor and Spitfire at the back, furthest from Burnscar.



Spitfire turned to run, and Burnscar drew together another fireball, lobbing it forward, where it soared high in the air before it began to drop.  The fireball collided with Spitfire, smashing the girl to the ground.  Flames licked off of her fireproof suit and the pavement around her, and it was long seconds before she was able to start pulling herself to her feet.



Burnscar drew fire up around herself, blinding the others, and in a moment, she was beside Spitfire, clutching the girl's throat with her fingertips, pushing her down against the ground that was still burning with traces of the fireball's heat.



\emph{Why couldn't this be one of the areas where the streets were flooded?  Why did Palanquin have to be on this hill?}



``Get her!''  Faultline shouted.  Shamrock drew her gun and fired, and Gregor launched a stream of slime toward the spot where Burnscar crouched.  The slime put out the flame where it landed, and in the moment the splashing slime and the billowing smoke obscured her, Burnscar disappeared.



``There!''



Burnscar had emerged from a patch of flames fifteen feet from Spitfire, and was striding toward the girl, ensuring Spitfire was in the way of any potential attacks from the rest of Faultline's crew.  She seized Spitfire and began dragging her toward an alley, one hand around her throat.  Wherever Burnscar stepped, she left burning footprints, and the flames slowly swelled and spread to join with one another, a trail of fire forming a path behind her.



Newter lunged forward, leaping over the flame that separated him from Gregor and then hopping to the nearest building to grab a bag of trash with his tail.  Twisting his entire body, he whipped the bag at Burnscar.  It struck her, and she staggered back, losing hold of Spitfire.



Burnscar dropped into the flames that covered the pavement and emerged from the flames just behind the others.



Elle, from the second floor room of Palanquin, banged on the window, trying to alert her comrades.



Like a flamethrower, twin streams of fire shot from Burnscar's hands, striking Shamrock, Faultline and Gregor.  Catching sight of the attack at the last second, Gregor did his best to shield Faultline and Shamrock with his bulk.  Newter threw more trash and rubble towards Burnscar, and succeeded in interrupting her assault on his teammates.



Faultline was on fire, her costume alight.  Gregor slimed her to put it out, then wheeled on Burnscar.



The same instant he turned towards her, the flame around her flared up, consuming her.



They turned to look for her, simultaneously trying to back away from the flames that spread with each of Burnscar's attacks, and they missed seeing the crouching form in their midst.  Only Elle, from her higher vantage point, was able to see Burnscar.



To say that Faultline and her crew were friends wasn't meaningful enough.  Elle saw them as \emph{family}.  And she was helpless to do anything to save them.



Her power was available to her, but the range was too small.  She needed time to soak it into an area, and she'd gone for a walk earlier.  Two hours since she'd gotten back, and her power was limited to her room, the neighboring rooms, the upstairs hallway and the exterior walls of the building that surrounded these areas.  Not enough to reach the street where the fighting was happening.  And if she moved beyond the boundaries, she would be losing ground.  Any time she moved to a new place, beyond the limits of where her power was taking effect, her area of influence shrunk to a few feet around her, only to start gradually bleeding out once more, faster with each passing minute.



She tried using it anyways.  Closing her eyes, she reached for the other worlds.



Pocket worlds, as she interpreted them.  Realities that were a blank canvas to be altered according to her thoughts, both conscious and unconscious.  They were lucid dreams that were big enough, detailed enough, intricate enough to swallow her up, as they so often did.  She could make new ones at a whim, but she found it better to build on what she already had.



There was the high temple.  Faultline and the hypnotist they'd hired had talked her through it, building a place that wasn't so influenced by Elle's negative thoughts and ideas.  It was a place she associated with personal triumphs, with her inner strengths.  At the opposite end of the coin was also the bad place.  Of the worlds, it was the biggest by far.  Nothing she could use there, she knew.  She was intimately familiar with every aspect of it.  She had spent a long time there.



Her eyes snapped open as explosion erupted in the street.  She saw Faultline, Gregor and Shamrock tumbling through the air.



Elle clutched her arms to her body.  The lonely hallways\ldots no.  The burning towers.  Definitely no.



The barren ruins.  She'd almost forgotten.  It had been her first attempt at making a world outside of the bad place.  It had worked up until the moment negativity and self loathing crept in through the cracks, filling in details where she didn't want them.  Ugly details.  What had resulted was a beautiful, solemn landscape rigged with traps and pitfalls, as if the landscape itself was eager to hurt or kill anyone who didn't watch their step.  As she focused on that world, a small part of her consciousness flew over the landscapes, an image in a second mind's eye.  Fields of tall grass, collapsed walls half covered in moss, the remnants of an old castle, a stone hut with a tree growing out of it.  She'd always had a soft spot for things that had once been beautiful but had transformed into a different kind of beauty as they aged.  She liked the look of a tree that had grown to splendor and then died, the statue worn by years of hard rain.  This was the aesthetic that had shaped the ruins.  Until everything turned ugly, unpredictable and dangerous.



Today was a good day.  She'd exhausted herself earlier in the week by taking on the Merchants on what she could easily mark as a bad day.  It seemed she was veering to the other side of things: she'd eaten, gone for a walk, even ventured to have a conversation with Faultline.  She could only do those things because her mind's eye, the gate to those other worlds, was nearly closed right now.  The drawback was that this also meant that the use of her power was slow.  As though she were looking through a spyglass, trying to find a distant detail, she could only take in one scene at a time.



She found what she wanted.  An age-worn statue of a woman in a toga, holding a large urn.  Focusing on it, she \emph{pushed}.



It was agonizing.  Not the use of her power – that was easy, unavoidable.  Even on a good day like today, her power worked without her asking for it.  The floor under her feet was turning into a stone tile, grass and moss growing in the cracks, as if the ruins were leaking into the real world.  It was agonizing because the emergence of the statue was \emph{slow}.  Brick folded out of the way as it appeared from within the outside wall of Palanquin.  It slid forth at a glacial pace of a quarter-inch every second, and it wasn't small.



The fire had spread across the street and to the wall of the building opposite Palanquin.  Burnscar was using it to travel great distances at a moment's notice, simultaneously spreading the flames further with every attack or spare moment she had.  Newter was quick enough to avoid her attacks while hurling objects at her to attempt to distract and batter her, but he couldn't approach to make contact with her and knock her out without her burning him, and his range of movement was quickly narrowing as the fires spread.  Not only were new patches of flame created when she attacked, but she frequently paused to will the existing fires to swell and extend further in every direction.



Gregor was hurt, but he was trying to control the spread of the flames, while protecting Faultline and Shamrock.  His skin glistened, which made Elle think he was covering himself in something that would protect him from being burned.



Her power was still so slow.  Only half of the statue had emerged.  Not enough.  She needed the entire thing.



Burnscar had noticed the statue, and paused to pelt it with fireballs.  Elle winced as the head broke free, felt a momentary despair as one arm shattered.  But the rest was intact.  Just two or three minutes.



Gregor caught Burnscar with a stream of slime, and the young woman disappeared in a swirl of fire.



Burnscar had appeared just behind Gregor, Shamrock and Faultline.  Before they could notice and react, she drew a ball of flame into a condensed point between her hands and released it in a violent explosion of heated air.



``No!'' Elle screamed, banging on the window.



Faultline wasn't moving, and Elle couldn't quite tell through the smoke that covered the street, but she might be burned.  Gregor\ldots Gregor wasn't moving either, and he lay in a patch of fire.  However fireproof the slime he'd coated himself in might be, he wasn't immune to being roasted.  Shamrock was limping away, limping towards the statue, and Newter was evading a fresh series of attacks from Burnscar.  Only Spitfire was largely untouched, helpless to do anything against an opponent that was not only fireproof, but who could walk through fires as easily as anyone else might use a doorway to move from one room to the next.



This wasn't right.  Her team, her friends, her family were all moments away from being obliterated.



She had to focus.  The statue wasn't enough.  She needed a mechanism.  The one that was attached to the statue in her mind's eye didn't work.  Something else.  She searched. A portcullis with a wheel\ldots no, too rusted, the chain too prone to snapping.  Ah, there.  A math puzzle, where a ball was set to roll down a series of tubes, with its path being determined by a series of levers, each moving a paddle that would adjust the ball's route.



So frustrating.  On her worst days, the days when her view of the other worlds was so expansive that she could barely register the real world, she didn't have to put things together like this.  She could shape things as she made them come into the real world, and they emerged as quickly as she wanted them.



Fitting everything into the statue, she had to use some of the math puzzle, the lever, some of the statue's existing mechanism, positioning it all so that they fit together as she pushed it into existence.



A fireball caught Newter in the stomach.  He was knocked from where he clung to the wall, falling to the ground.  He had to roll out of a patch of ground that was licked by orange flame.



Burnscar turned to Shamrock, who was waiting for the lever to emerge.  A fireball was flung at the red-haired woman, who ducked too slowly.  The flame clipped her in the shoulder in its route to punch a hole in the wall, directly where the lever was.  Pieces of the mechanism tumbled around Shamrock.  Gears, levers, paddles and fragments of the switch.



``No!''  Elle shouted, ``No!''



Her effort had been for nothing.  Could she cobble something else together?  Would it matter?  Their opponent had an idea of what Elle wanted to do.  She wasn't going to offer the opportunity.



The last piece of the math puzzle emerged within the brick walls of Palanquin.  Two inches across in diameter, the ball fell along its set route.  Rolling down a slight slope, dropping through one spot where the paddle was pointing down, landing on the next slope, rolling in the opposite direction, over two paddles.



Elle grabbed her chair and shattered her window.  Gripping the sides of the window, ignoring the glass that bit into her fingers, she screamed, ``Shamrock!''



Both Shamrock and Burnscar looked up at her.



She slapped the wall with her hand, leaving bloody fingerprints where the glass had cut her, ``The ball needs to go right!''



Burnscar launched another fireball at Shamrock, and Shamrock leaped to one side.



``What ball!?''



Elle couldn't tell her, not without letting Burnscar know.  She could feel the ball making its way down the last slope, dropping down the far left, to where the mechanism and the lower half of the puzzle had been devastated by Burnscar's fireball.  Shamrock would get a glimpse of the ball through the hole in the wall, as it dropped down\ldots \emph{now}.



Elle felt the almost imperceptible influence of Shamrock's power.  The woman was a telekinetic and clairvoyant on the smallest of scales, capable of making small changes and knowing how to use them to make big things happen.  The ball moved a few millimeters to the left, hit a splinter of wood and bounced toward the right, spinning.  It landed, and the spin of its rotation coupled with the help of an additional nudge carried the ball to the right, and down into the chamber behind the statue.



There was a rumble, and water began pouring from the stump of one arm and the urn the statue held.  It poured down around Shamrock, flooding out onto the street to quench the fires on the ground level.  Soon it was only the patches of flame on the walls that remained.



Shamrock raised her gun, aiming at Burnscar, and fired.  Once, twice.  It was hard to tell if the shots hit home, because Burnscar was already wreathing herself in flame, disappearing to appear from the burning wall nearest Spitfire.



Spitfire ran, and Burnscar chased her.  Elle could see Shamrock hesitate, then leap through the curtain of water that poured from the urn, giving chase, hoping to help her teammate.



``No!'' Elle shouted.  But her voice was drowned out by the sound of the water.  Soon the pair were gone.



Her phone.  She needed to phone them, let them know.  Where was it?



In the kitchen.  \emph{Stupid}.  She'd been in one of her momentary fugues when they'd been gathering dinner, she had to have left it there.  And if she ventured any further than the upstairs hallway, maybe the ledge above the dance floor, she would be losing any ground she'd gained with her power here.



A horn\ldots some kind of noisemaker.  A bell?  There was a bell in one area of the barren ruins, if she could only find it.



Burnscar dropped from the burning wall opposite Palanquin.  Retracing her steps.  She looked up at the window that Elle stood behind.



\emph{She's not after Spitfire.  She's after me}, Elle thought, with a moment's despair.



Burnscar trudged through the expanding pool of water to enter Palanquin's front door.  The club was empty, there was no power, no music.  Even the employees were attending to their personal lives.  It was just Elle and Burnscar.



It was a minute before the door to her bedroom opened.



``There you are,'' Burnscar said.



Elle looked away.



``Hello, old friend,'' Burnscar said.



She wasn't good at talking, even on a good day.  ``Mimi.''



``Long time.''



Elle nodded.



``I'm\ldots I'm sorry about your friends.  I didn't come here planning to do that.  It's just\ldots you know.''



Elle nodded, trying to keep her outrage off her face.



``I- Fuck.  I'm really sorry, you know?  I can't help it.''



\emph{You can.  You just don't try hard enough.}



But Elle didn't voice her thoughts.  She nodded.



``I don't think I did any permanent damage.  They're alive.''



``Thank you,'' Elle managed.  She couldn't entirely suppress the bitterness in her voice.  Burnscar didn't seem to notice.



``I- I wanted to talk.  Like old times.''



\emph{Old times}.  Elle couldn't help it.  Her thoughts turned to the bad place, the biggest of her worlds, the world she had spent the most time.



``Back when we were both having our good days?  We'd talk, and I really liked those times.  I look back on them fondly.  One of the few moments I treasure.''



Elle nodded.  Behind Burnscar, the door to her room was changing to metal.  A tiny window was expanding, bars already closing down like teeth.  The wall around the door was growing tatters of cloth that rippled like they were blowing in the wind.



``Fuck,'' Burnscar said, ``I don't even know where to start.  Since I learned you were in this city, and the group wanted to come here, I've been looking forward to this, seeing you again, but now I don't know what to say.''



``The weather?'' Elle tried, lightly joking. The wrong thing to say.



``I don't want to talk about the weather!'' Burnscar snapped the words, in a mixture of desperation and anger.  Her eyes flashed orange and flame flared around her hands, then it all faded.



``Sorry.''



``I\ldots um.  How are you?  How have you been, since you escaped?''



``Been\ldots been good.  Good people.''  \emph{So hard to articulate my thoughts, even on a good day.} ``They take care of me.  Faultline helped\ldots more than any doctor I've had.''



``The doctors,'' Burnscar scowled.



``You?''



``I\ldots did you know I escaped at the same time you did?''



Elle shook her head.



``I did.  But I had no place to go.  I had some bad days.  I was lonely, scared.  Some guy tried to convince me to be his whore, earn some cash, get fed\ldots I refused, but he kept coming after me.''



``Sorry.''



``I\ldots I really wanted to be good.  I'd told myself I wouldn't use my power.  But I had to protect myself, you understand?''



Elle nodded.  The cloth around the door had started to settle into a shape.  Padded walls, lined with barbed wire and jagged rows of glass.  There were stains of shit and blood on some of the cloth, now, growing and swelling.  She tried to will it to stop, to focus on her high temple.  Her safe place.  But looking at Burnscar, that place felt so far away.  It was out of her reach.



Burnscar went on, ``So I used it to scare him off\ldots but you know how it works.  You know what happens with my power.''



``I remember.''



``I\ldots the doctors say that using my power, it adjusts the chemical balances and connections in my brain.  Empathy, impulse control, my emotions, they disappear as I use my power, and I can't \emph{help} using my power if there's fire nearby.  It snowballs, because I use my power more when I don't have that self-control, when I don't care about the people I'm near, and when I'm in that headspace I don't want to leave it.''



``Yeah.''  \emph{And you retreat into that state to avoid facing the guilt over things you've done.  You use it to hide from your own fears.  If I blame you for anything, it's for that}.



Burnscar shook her head.  ``If you hadn't put out most of the fire out there\ldots I dunno what I would have done.''



\emph{I have a pretty good idea.}



``So I burned the pimp to scare him, then I burned him to hurt him, for payback over his hounding me, and then I couldn't really stop myself.  I burned him to death.  Fuck. That was the start of a bad few weeks.''



``Sorry.''



``I- before I knew it, the Slaughterhouse Nine had found me.  Shatterbird recruited me.  And now I'm stuck.  I'm trapped.  You know there's a kill order out on me?  If I try to quit, either the Nine or the cops will off me.  So I keep going, I work for them, and it all just gets worse.''



``Surrender?  Go to the birdcage?''



``They'd \emph{find} me.  You don't even know what these guys are capable of.  Our newest member, she replaced Hatchet Face, though he's still around\ldots kind of.  She can \emph{find} people.  There's no place secure enough to keep me safe until they took me to the Birdcage.  I almost think they'd be able to get me in there, if they wanted to.  Siberian?  She'd be able to get me.   Even in the Birdcage.  She \emph{always} gets her prey.''



``Can't keep hurting people, Mimi.''



``I \emph{have} to.  I- I can just use my power.  Stay in that headspace where I don't feel bad, where I act the way the Nine expect me to.''



The bad place was intruding on the room further.  Elle spoke up, ``Mimi\ldots  Can I touch you?  Anchor you?  Don't want my power to hurt you.''



``So you want to keep me out of your world?''  Mimi smiled and shook her head.  ``No way.  Half the reason I came here was because I heard you were making beautiful things these days.  I have to see it.  The things you can make, now.''



Then she turned and looked around.  Her face fell as she saw the padded walls, the bed that had become a cot, the shit stains, the blood, the needles in the corner, the broken glass and the razorblades that were embedded in every surface, waiting to catch anyone unsuspecting that put their hand or foot in the wrong place.



``No,'' Burnscar said.



Elle tensed.  ``Sorry.''



Burnscar's face fell.  ``This\ldots this isn't beautiful.  I remember this.''



``Would show you the others\ldots if I could.''



Burnscar's voice was choked.  ``But you can't.  Because I remind you of the asylum.  I remind you of the bad times, the times you were most miserable.''



Elle looked down at her feet, swallowed past the lump in her throat.



``I thought we were friends.  We had our moments, didn't we?  Only a few times, when we were both allowed out of our cells, when we were having good days.  A few jokes, stories.  I mean, I know that some of the time I was coming off a bad spell, so maybe I snapped, or I called you names, or threatened you\ldots''



Burnscar trailed off.  Elle stayed silent.



``It.  It wasn't, um.'' Burnscar stuttered.  Her eyes flashed orange.  ``Did \emph{you} see \emph{me} as a friend?  Don't you dare lie to me.''



Elle couldn't come up with a reply.  \emph{They used me as an enticement to get you to cooperate.}



``Oh fuck.  Fuck me, I'm sorry,'' Burnscar said.  She turned away, fumbled with the metal door.  Elle realized it had locked, adjusted things to allow it to open.  Burnscar pulled it open, then stopped in the doorway.  Her back turned, the girl said, ``I'm sorry about your friends.  I really hope they're okay.''



``I do too.''



``I'm glad you're doing well.  I hope I didn't fuck everything up.''



It took a bit of courage, but Elle hurried to cross the room and wrap her arms around Burnscar, hugging her from behind.



``We had some good times,'' Elle lied.  ``Take care.''



Burnscar pulled away, and Elle let the girl go.  She saw Burnscar find the door to the indoor balcony that overlooked the dance floor, heard her run down the stairs.



Elle sank down against the wall, pushing away the sharp things that would cut her with a use of her power.  She put her head in her hands and closed her eyes to the sights around her.  She'd wait a few minutes.  She'd take a few minutes wait until she could be sure Burnscar was gone, then she would leave to check on the others.



It would be weeks before she had made up for the ground she had just lost, in terms of her mental health, in pushing past the bad memories and the bad place.  She reassured herself with the thought that she would get better, in time.  She'd gotten there once, she could get there again.  If the others were okay.



As for Burnscar?  There would be no helping that girl.





