





There was a faint tapping sound.  A clink of something hard on metal or glass.



It came again, a second later.



Colin looked up from his computer.  Ears peeled, he turned his head to the left and waited.  Clink.  He turned his head the other way, in the hopes of pinpointing the source.



He heard a scraping noise, then the sound once more.  He couldn't say where it came from.



He opened an instant message window on his computer and sent a message:



\strong{PHQ.Armsmaster:}  You have a sec?



\strong{Guild.Dragon:}  Reading the most monotonous data on seismic activity and Behemoth's possible movements.  Ugly code.  Distract me, I beg you.



\strong{PHQ.Armsmaster:}  Hearing something.  Can you listen in?



A few seconds passed, then it came again.



\strong{Guild.Dragon:}  I hear it.  Wait.  Changing the settings on your microphones so I can triangulate the source.



As casually as he was able, he glanced towards the window.  Tinted glass, bulletproof, and reinforced with a low degree forcefield.  It would be easier for someone else to go through the wall than the window, but he couldn't see through walls.  Nothing outdoors.  Just an overcast sky hiding the majority of the moon, and a faint drizzle of rain.  No person or animal, nothing else.



Clink.



\strong{Guild.Dragon:}  Vent, behind and above you.



He whirled around, grabbing the model of his nanobranch disintegration weapon from the stand on his desk.  It was miniaturized, a mere pocket knife that Piggot could use for demonstration.  Still, it would serve better than any chair or tool he might pick up.



He briefly debated going for the helmet with the link back to his old suit's combat analyzer.  But it wasn't set up, it would cost him precious seconds – twenty or thirty – before he connected to the main server.  Until that happened, the helmet would only render him blind.  A blank display.



Something moved in the gloom behind the vent.  There was a flash of something white or light gray, and the vent rattled, a puff of dust flowing down where the screws held it in place.  Again, there was the sound.  Clink.



The vent exploded from the wall with enough force to fly across the room and embed in the opposite wall. It was hard to make out in the cloud of plaster dust, but Colin saw a hand, all white, each joint segmented, fingers splayed, palm facing the room.



The hand tipped forward, and then dropped to the floor alongside the attached forearm, a length of chain stretching from the vent to the `elbow'.



Other body parts followed, each separated from the rest, encased in a white shell.  An upper arm, two halves of a torso, then a head.  The rest of the body followed, flowing to the ground like a liquid to pool there.  The right arm and the left leg were separate, detached, with only ball joints at the end.



Colin noted that the flat expanse that would join the left side of the chest to the right had a clear pane to it.  Organs were inside, cut cleanly down the middle, and they pulsed with activity, throbbing wet against the glass or glass substitute.  There was technology in there too.  Regulators and filtration systems, and other gear that was designed to fit into the gaps between the most vital systems.  Weapons, tools.



He knew this one from the briefings.  Mannequin.



The realization of what he was up against spurred him to action, pushed him beyond that momentary paralysis that came with the grim sight of the internal organs.  While Mannequin was incapacitated, he charged, clicking a switch on the handle of his knife to activate the disintegration effect.  A static grey cloud formed around the knife.



Colin was two paces away when a telescoping blade speared out from Mannequin's hand, straight at him.  It was luck as much as reflexes that let him stop his run, his feet sliding on the smooth ground, before he ran into the weapon.  He dropped onto his back, instinctively rolling with the fall to reduce the impact.



The blade snapped back into Mannequin's hand with enough force that the hand and forearm it was attached to recoiled from the impact.  It flipped into the air, and the blade snapped out again to impale the top of the door frame.



The chain retracted with a faint whirr, and the forearm snapped into place on the upper arm, which soon connected to the shoulder of the torso.  The chain joining the two halves of the torso together reeled in and locked into place by way of some unseen mechanism, the seam between them almost invisible.  Colin felt a faint tug from his weapon as some electromagnetics kicked into effect.  The unattached arm and leg flew to the shoulder and pelvis and snapped into place.



The head was the last thing to join the tall, thin body.  The chain slowly reeled it in, dragging the head along the floor, lifting it off the ground.  It swung, bouncing off one leg, the stomach, then the shoulder before it finally connected to the neck, the very top of the head scraping the ceiling.  There were no eyeholes, no earholes, nor any vents for air intake.  There was only a head as white and smooth as an eggshell, with shallow indents where the eyes and mouth should be and a small bump for the nose.



Mannequin raised one hand and placed it on the top of his head.  With a sharp twist, he snapped it into place with an audible click.  He tested the range of motion, tilting it forward, backward, to either side, then spinning it around three-hundred-and-sixty degrees.



``Dragon,'' Colin whispered, ``Are you getting this?''



``Help is on the way, Colin.''  The whole room was outfitted with speakers, microphones and microcameras.  Her voice came from the speaker directly behind him, so quiet that he would have thought he imagined it, if he didn't know her.



Mannequin tested the rest of his body, while Colin slowly climbed to his feet.  Every joint was too flexible, and was capable of moving in every angle.  For a moment, Mannequin's fingers were like worms, each knuckle bending in impossible directions.



Was the killer hoping to intimidate him?  Nobody would test these mechanics in front of an enemy, so this was most likely a demonstration.



Four blades sprang from Mannequin's left forearm.  The limb began to rotate, slowly at first, then faster, until the four blades were whirling like a helicopter propellor.  Colin tensed, preparing to jump the moment the limb shot towards him.  He'd never wanted his suit so badly.



The propeller-like whirl of the blades gave the arm some buoyancy, and it shifted enough to come into contact with Mannequin's leg.  All at once, it ricocheted, shearing through the computer, bouncing violently off of Mannequin's head, then his leg again, the desk, then his arm.



Colin watched every movement of the bouncing blades, waiting for the moment it would fly free, or the second Mannequin charged.  There would be no dodging that unscathed.



But Mannequin didn't move.  The spinning slowed, and the whirling blades settled into a rhythmic bounce against Mannequin's leg, until it had stopped entirely, the arm swinging gently.  The blades retracted.



Mannequin didn't speak, he made no sound.



Long moments passed.



``Talk to me, Dragon,'' he murmured.  His voice shook just a touch.  Any second now, Mannequin would cut to the chase and attack, and he could die at this monster's hands.



Her voice was quiet behind him.  As much as anything, it helped keep him calm.  ``Mannequin.  Original name Alan Gramme.  Tinker, originally went by the name Sphere.  Specialty is in biomes, terraforming and ecosystems\ldots or it was.''



Colin nodded slowly.  He knew this, but it was reassuring to get a recap.



``He became newsworthy when he took on a project to build self sustaining biospheres on the moon.  He had ideas on solving world hunger, and building aquatic cities near cities plagued by overcrowding.  And he was putting it all into effect.  Until--''



``The Simurgh,'' Colin finished.



``His wife and children were killed in the attack, years of work ruined.  Everything fell apart.  He went mad.  He cut himself off from the rest of the world.  Literally sealed himself away.''



Colin looked at the cases that surrounded each individual body part.  Each body part a self-contained system.  Everything nonessential stripped away and replaced.



Her voice was even quieter than before as she said, ``He has a body count, Colin.  You know\ldots''



She trailed off, unwilling to finish.



``I know,'' he finished for her.  Like other serial killers, Mannequin favored certain types of people as victims.  His prey of choice included rogues, those individuals seeking to make a profit from their abilities, especially those looking to better the world\ldots and tinkers.



Mannequin swayed slightly on the spot.  Like a doll with a broken neck joint, his head flopped onto one side, until it was perpendicular to the floor.  There was a click as he slowly righted it.



``What do you want, monster?''  Colin growled, ``Little point in coming after me.  I don't have much of a life to look forward to.  I've already lost everything!''



Mannequin didn't move.



``You'd be doing me a fucking favor!'' Colin shouted, ``Come on!  Come get me, you freak!''



There wasn't a movement or sound from the killer.



There was a sound from Dragon.  In a tone that was afflicted with agonizing disappointment, like a mother who had just found out her son had been arrested for a felony, she said, ``Oh, Colin.''



Colin didn't speak.  He waited for elaboration.



``The PRT got a tip from one of the villain teams.  The Slaughterhouse Nine is in town.''



``So I gathered.''



``They ran it by some of the experts.  Colin, the consensus they came to was that Slaughterhouse Nine are in Brockton Bay to replace their ninth member.''



He stared at Mannequin, and the realization made his blood run cold.



``Me!?'' he shouted.



The faceless man cocked his head to one side.



Colin roared, ``I'm a fucking soldier!  I made a call that could have saved millions of lives!  Billions!  You're ten times as fucked up as I thought you were if you think I belong in your group!''



Uncaring or oblivious to the outburst, Mannequin turned and examined the ruined computer.  He picked up a key that had been thrown off the ruined keyboard and turned it over in his fingers.



``Listen to me, you psychopath!''



``Colin!''  Dragon's voice hissed from the speaker, not as quiet as it had been.  ``Don't provoke him!  Help is nearly there!''



Colin had to stop to control his breathing, and he bit his tongue to keep from saying anything further.  His enemy had to have heard her, but didn't seem to care.



Mannequin fished through the broken keys from the keyboard, found another, and folded one finger back to pin it against the back of his hand.  He ejected a blade from his wrist and used it to scrape the letters that were still intact off the board.  They clattered to the desktop, and a few fell to the floor.



The featureless white head swiveled one way, then the other.



After a long moment, one arm dropped to the floor, the chain going slack.  The hand crawled over to pick up another key, then the arm reeled in.



Colin tensed as Mannequin approached, backing up as far as he was able  The window was just behind him now, and he could almost imagine the crackling of the rainwater vaporizing against the forcefield.



The villain turned and placed the keys down on the edge of Colin's desk.  The first key was the letter U.



Six inches away, Mannequin put down an M, sideways.  He corrected it so it was upright.  Directly beside it, the villain put down an E.



He stepped away from the desk and faced Colin once more.



``You\ldots me?''  Colin asked.



Mannequin cocked his head.



``Is this a riddle?''



Mannequin swiveled his upper body to face the other direction and reached for the shattered monitor.  He picked out a piece of glass and a piece of glossy black plastic.  Pressing them together, he raised it to the right side of his face, looking down at Colin.  Slowly, Mannequin changed the angle of the shard of glass with the black backing.



It took two long seconds before the villain's intent became clear.  Colin tensed, and Mannequin froze, fixing the angle of the shard.



With the black backing, the glass reflected an image.  With the angle Mannequin had carefully found, the image reflected was half of Colin's own face, overlapping with Mannequin's head.



``No,'' Colin muttered.



``Quiet!''  Dragon's voice whispered from the nearby speaker, ``They're in the building, they'll be there to help you in two minutes, maybe less!  I can see them on the security cameras!''



``I'm nothing like you!''  Colin screamed at the villain.



Mannequin stared at him with the shallow, empty eye sockets.



``I didn't date, I didn't have kids, because I wanted to be out there, helping!  I knew that any attachments could be used against me, so I went without!  I was fucking smart enough to do that!''



``Colin!''  Dragon pleaded.  Her voice was louder.



The villain didn't move.



``Fucking answer me!  Spell the fucking words with keys if you have to!''  He roared the words at the mad tinker.



Mannequin swayed slightly, then righted himself with a sudden, jerky motion, as if he'd collapse into a heap if he wasn't careful.  He used his hand to shift his back into place with an audible click.



Colin went on, ``I was out there every day, helping.  I took steps to fight evil and take down criminals every day, small steps, baby steps.''



``Colin, stop, please!''



Dragon's words didn't matter.  He was going to die anyways.  He'd known the moment he recognized Mannequin.  He'd go down fighting, hurt this motherfucker the only ways he could.



``You want to compare us, freak?  Maybe we both had bad days.  Days where nothing went right, days where we were too slow, too stupid, too weak, unprepared or tired.  Days we'll look back on for the rest of our fucking miserable lives, wondering what we would have done different, what we could have done better, how things could have played out.  The difference between us is that I actually did something with my life, and I'm still trying to do more while I serve my sentence!''  He stopped and took a breath.  ``You started your big projects, got every fucking person in the world to get their hopes up, and then you failed to finish \emph{anything} because you couldn't hack it when your fucking family got killed!  You insult their fucking memories every motherfucking second you exist like this!''



Mannequin slammed him into the wall with more strength than he might have expected the artificial body to have.  The blade came next, springing from Mannequin's hand to pierce the shoulder that led to Colin's stump of an arm and stick through the wall behind him.



The villain withdrew the hand, then punched the blade into Colin's stomach.  Once, twice, three times.



Dragon's scream came from every speaker in the room.



A slash of the blade caught Colin across the face, blinding him in one eye and tearing through the bridge of his nose.



None of it hurt as much as it felt like it should have.  More serious wounds didn't tend to, odd as it was.



Colin tried to laugh, and found he couldn't.  He could feel blood flowing into his mouth and throat through the gaping wound in his face.  He let his head hang forward, so the blood could mostly flow out of his mouth.



He tried to move forward, lunge with his knife, but he couldn't pull his shoulder from the wall, even though the blade was no longer pinning him there.  Was it a lack of physical strength, or something mechanical, flesh and bone shoved into the hole in the wall?



Couldn't lapse into that kind of thinking.



Still had the knife.  One hole in the self-contained systems that were one of Mannequin's vital body parts would cause a leak of fluids, an introduction of pathogens that Mannequin surely wouldn't be able to fight off.



He tried to speak, but there was too much blood in his mouth, and he only managed to start coughing violently, spraying blood on the white of Mannequin's chest.  His vision was getting hazy.



He wouldn't be able to distract the lunatic with words while he acted.  He could only pray.



\emph{Don't do it for me, God.  I probably don't deserve the chance.  Do it for every soul this motherfucker would kill from here on out if I fail.}



He thrust out the knife, swept it towards his opponent's chest cavity.  His hand stopped.



With his vision in his good eye failing him, it took him a second to see why.  Mannequin's hand gripped his wrist.



He pushed, as if he could beat this monster in strength.  By some miracle, his hand moved a fraction closer to his enemy's chest.  He redoubled his efforts, and it moved still closer.



A blade stuck out of Mannequin's upper arm, near the elbow joint.  The upper arm fired like a small rocket to stick in the wall, and for a second, there was slack in the chain.  Colin thrust the knife forward, came within inches of making contact with Mannequin's chest before the chain reeled in and the metal links went rigid.



The chain started to gradually reel in, and Mannequin started pulling his hand backward, toward the wall where the section of arm had stuck.



Then, as if to taunt Colin, Mannequin dropped to a crouch, moved his face less than an inch from the blur that marked the edge of the blade's effect.



\emph{No!}



He couldn't say where, but he found some reserve of strength.  The knife inched closer.  Hairs away.  He could see the material of the casing smoke just beneath Mannequin's `eye', a dark patch revealing itself beneath.



Mannequin's head fell, tipping over backwards to strike the ground, dangling from the chain, out of reach of the blade.  Still holding Colin's wrist, the headless villain stood straight.



\emph{He was toying with me.}



Mannequin wrenched his hand back, as if to make it clear that he had \emph{let} him get that close, that Colin had never really stood a chance.  Colin was pulled to one side, and he didn't have the strength in his midsection to keep from falling over.  His knife clattered from his grip as he fell to the floor.



The villain picked up the knife, examined it, then pressed the button to test it.  The last thing Colin saw before darkness consumed his vision was the bastard using the weapon on the wall beside the window, dust billowing where it made contact.



In the last seconds of consciousness, he heard Dragon's voice, as if from a far away place.  ``No!  No, no no!  Colin!  Stay awake!  I need you!''



\sectionbreak



Her voice was the first thing he heard when he woke.  ``Welcome back.''



``I survived,'' his voice rasped.  He'd had a tracheotomy.  The only explanation for his throat being this sore would be having a tube rammed down it.  Looking around, he saw a laptop propped up beside him, and a get well card from Miss Militia.  She must have put the laptop there when she left the card.



``Your heart stopped nine times on the operating table,'' Dragon said, ``A lesser man wouldn't have made it.''



``How?''



``Artificial parts.  I supplied your headquarters with a 3D scanner of my design weeks ago.  I had them make the parts I specified.  The on-site doctors kept you alive long enough for the scanner to make the necessary components, and they followed my instructions in installing them.''



``Good girl,'' he told her, with genuine affection.



``I'm sorry about your face.''



He tried to raise his hand, but found it attached to IVs.  He had to maneuver it carefully as he lifted it to his face, so as not to tangle the wires.  Almost seamlessly, his flesh transitioned into a smooth plastic and back to flesh again.



``It's alright,'' he said.



``Your new eye doesn't work.  I think I know what's wrong with it, and I can get you something that will work, I just need time.''



``You have better things to be doing.''  He coughed and regretted it as pain ripped through his throat with the movement of the muscles.  His stomach felt strange.  He started to speak, cleared his throat, then said,  ``I think I could pull off an eye patch.''



``The parts won't last.  All of this is prototype stuff.  Some of it I revised and invented while you were in surgery.  They're temporary, but I can make better.  I'm afraid you're going to need to go under the knife a few times.  More than a few.''



``That's fine.  Thank you for all this.''



There was a pause.



``You're a fucking idiot, Colin.  That was the stupidest fucking thing I've ever seen.''



He laughed.  His breath caught with the pain each laugh produced, but he couldn't help it.



``Yeah, I hope that hurt.''



``Wanted to provoke him.  See if I couldn't find an opening.''



``I repeat: Stupidest fucking thing I've ever seen.''



``Was going to kill me anyways.''



``Was he?  He could have killed you there.  He didn't.''



``He tried.''



``No, Colin.  Look.''



The laptop screen on the table beside him lit up, and a browser page opened.  An image loaded.



A photo.  Mannequin had left a message.  3 keys, again, on the edge of the desk.  BR8.



The eight, Colin supposed, was meant to stand in for a second B.  `BRB', an acronym used by countless denizens of the internet and innumerable cell phone texters.  Be Right Back.



``Could be meant for you guys.''



``Or it could be for you.''



``He left me for dead. He couldn't really expect I'd survive.''



Dragon didn't reply.  He thought of Mannequin.  Despite the silence, despite the uncanny behavior and the dramatic self mutilation, Mannequin was a \emph{brilliant} man.  A man who could have looked at the resources that were available in the building, who could have figured out Colin was in touch with Dragon, done \emph{just} enough damage to push him to the brink of death.



``Shit.  He probably\emph{ could},'' Colin conceded.



He stared at the photo for several long seconds, then turned away.



Hoping to inject some levity into the grim conversation, he smiled and asked her, ``What was this I heard when I was passing out?  `I need you'?''



The silence stretched on for so long that he knew he'd made some faux pas.  He just wasn't sure what.  Stupid.  This was the kind of thing that had cost him his position, started the dominoes falling in such a way that they'd led him to being prisoner in that room, led to him being an easy target for Mannequin, to him being here, in this bed.  Never knowing what to say, or how to say it, or who to say it to.



He was about to apologize when Dragon said, ``Those prosthetics I gave you?  They were part of a bigger project.  Something I'd intended to use for myself.''



She was a cripple?  He'd known she had survived Leviathan's attack on Newfoundland, was it such a surprise that she'd gotten hurt then?  It would explain her aversion to showing her face.  One of the things she'd given him was a facial prosthetic.



``I'm sorry,'' he said, ``I didn't know.''



``No, it's not that,'' she paused.  ``There's something you need to know about me.''





