





The high-pitched song of steel rang through the air as sword parried sword, struck shield and fell to the ground.  Somewhat less sweet were the guttural grunts and muffled slaps of flesh being battered and struck.  A boot in the stomach, an elbow or fist striking a face.



Hookwolf walked between the groups of his sparring recruits.  They were tired, pushing themselves through their exhaustion.  All wanted to be here.  The training was too punishing for anyone who didn't.  With small exceptions for eating and sleeping, their days were filled with exercise, hand to hand sparring, gun training, and practice with melee weapons.



The main adversaries of the Chosen were mercenary soldiers, police and trained heroes.  Why should the standards of his Chosen be any lower than theirs?  No, if his group was to represent the true Aryan warrior, they had to have \emph{higher} standards.  They had to be the best.



It was that knowledge, that commitment that drove his trainees to give their all.  Too many saw the Aryans as hatemongers, failed to see the greater picture, the hope for raising humanity to a higher level.  He stopped at one end of the room to watch their progress, watch for the ones who had the \emph{killer instinct} he needed.  Stormtiger and Menja were at the other end of the room, looking for the same.  Stormtiger had cast off his mask, and wore only face paint.  He still walked a little stiffly from the gunshot wounds that he'd taken to his legs.  Othala had attended to them over the past few weeks, would give him a half-hour to an hour of regenerating ability each night until he was better, but knees were slow to heal.  Menja wore her armor, her expression stern as she watched the form and habits of the combatants.  Cricket sat in one corner of the room, typing on a laptop without looking at the screen, taking notes on the trainees.



Hookwolf looked at Menja, and she raised one hand, two fingers extended.  Signalling, she pointed to two of his thirty-four recruits.  A bald man in peak physical condition and a twenty something girl with the ends of her hair in thin bleached blond braids.  A little too much like cornrows for his liking.  Maybe it was supposed to be ironic.  He liked her first pick, though.  He'd noticed the bald man.  He'd committed their names to memory on first meeting them, but he'd forgotten some.  He knew the man was Bradley, the girl was Leah or Laura or something like that.  His own pick was a lean scrapper in his early thirties, Ralph.



``Stop!'' he ordered.



As one, his recruits pulled away from their fights and sheathed their blunted swords.  Not all of them were able to stand straight.  More than a few had bloody noses or black eyes.



``You're three days into our week of training.  If you're still here, you're doing us proud.''



He could see a few of them stand a little taller at that.  Hookwolf had been a fighter before he'd been a fighter with powers.  He had spent a great deal of time around athletes, knew all too well that just a little recognition and a little motivation could make a world of difference.



``Some of you have earned special attention.  You've fought harder, meaner or \emph{better} than the others.  Bradley, come here.''



The bald man approached.



``Menja.''



Menja stepped through the gathered recruits to stand beside Bradley.



``You two are going to fight.  No weapons, no armor.  Menja?  You can use your powers, just a little.''



Menja smiled, then she grew a foot and a half.  Bradley stood at a height of just over six feet, but she still loomed head and shoulders above him.  She unstrapped her armor and threw it aside.



Bradley looked at Hookwolf, a flicker of concern crossing his features.



``Part of the reason for this is that I want to see how you do against someone bigger than you,'' Hookwolf said.  ``You're tired.  You've been training and sparring all day, Menja hasn't.  Tough.  If you're going to represent the Chosen as one of our elite, you're going to be expected to go up against capes.  Things will be just as one-sided or worse.''



Bradley looked to his left, sizing up Menja.



``Think you can fight her without embarrassing us?  If you think you can do it, you might just have a place as one of our lieutenants or as a leader of one of our warbands.''



``I'm no coward,'' Bradley replied.  He turned to Menja and adopted a practiced fighting stance.



Hookwolf watched with approval as the two squared off.  It was clear from the start that Bradley was thrown off guard by how strong Menja was, and doubly apparent that he wasn't used to fighting someone with better reach or more power behind their hits.  But he was trained, and he was familiar in how to use his body, and he adapted quickly.



Bradley shifted to the defensive, and Menja struck with sharp kicks to his side and lunging steps forward to jab at his face.  He timed a grab and quickly shifted to an arm lock, forcing Menja to bend over.  For just a moment, it seemed like he had control of the situation, but Menja snapped back to her normal size, slipping her arm free, then struck at him, simultaneously growing.  He was shoved to the ground.



``Enough,'' Hookwolf said.



It wouldn't do to let the man defeat Menja, and it was looking increasingly possible that he might.  It would hurt her pride and weaken the position of his powered lieutenants in comparison to the unpowered ones.



``Good man,'' he said from behind his mask.  He offered the man a hand, and Bradley took it.  ``Well done.  Welcome to the Chosen's elite.''



Bradley nodded and stood at attention.



Hookwolf turned to the blond girl. ``Leah, was it?''



She looked surprised to be picked, but she nodded.



``Menja likes you.  I don't.  You get one chance to prove me wrong.  Menja?  Who would you set her against?''



There weren't many options.  Stormtiger couldn't walk, Menja wouldn't nominate herself, and it wouldn't just be a hassle to go get Rune, Othala or Victor, but each of the three were either too powerful in a brawl or effectively powerless.  That left Hookwolf himself and-



``Cricket,'' Menja said.  ``Same reasoning.  Leah's quick, Cricket's quicker.''



Cricket stood from her seat in the corner and limped forward.  She'd refused the same help that Othala had granted Stormtiger, both for the injury to her leg and the damage she'd taken to her vocal chords when she'd had her throat slashed, in a time before he'd met her.  It would have taken a few days at most to restore her to peak condition, but she valued her battle scars too highly.



``Up for this, Leah?'' Hookwolf smiled.  Cricket's injury to her leg slowed her down some, but the young woman was anything but a pushover.



Cricket reached to her side and picked up a small silver tube.  She pressed it to the base of her throat, and her voice came out sounding distorted and digital, ``Something's wrong.''



``With the fight?''  Hookwolf asked, raising one eyebrow.



Cricket opened her mouth and pressed the tube to her throat to reply, but didn't get a chance.  The windows shattered with an explosive force, knocking the majority of the people in the room to the ground.  Hookwolf was one of the few to remain standing, though he bent over as shards of glass tore through the layer of skin that covered his metal body.



He took a moment to compose himself in the wake of the blast.  His ears rang, and he bled from a dozen cuts, but he was more or less fine.  His people were not.  They groaned and screamed in pain, accompanied by the sound of car alarms going off outside.



Two trainees and one of his graduated Chosen were dead.  They'd been wearing glasses, and the glass had penetrated their eyes to tear into their brains.  The others were all wounded to some degree or another.  Some had been hit by the glass that flew from glasses others were wearing, others from the windows, and one or two others had patches of blood rapidly expanding around pockets where cell phones had been stowed.



Why couldn't they have put the cell phones away before they started sparring?



Leah lay dying, and Stormtiger had one hand pressed to his throat, blood billowing from a cut that may or may not have nicked an artery.



Hookwolf tapped into his core, the `heart' from which his metal sprouted inside his body.  He could feel it start to churn with activity, and the metal he already had encasing each of his muscles began to stir.  Soon it was lancing in and out of his pores, criss-crossing, some blades or needlepoints sliding against others with the sounds of whetted knives.  In a few seconds, he had covered his body, to protect himself from further attacks.



``Shatterbird!'' he roared, once he knew he was secure.  There was no reply.  Of course.  She was attacking from a safe position.



An attack from her meant an attack from the rest of the Slaughterhouse Nine.  Daunting, but not impossible.  He was virtually invincible in this form.  That left few that could actively hurt him.  Burnscar.  The Siberian.  Crawler.  There was Hatchet Face, the bogeyman of capes.  With the exception of Hatchet Face, the group wouldn't be able to do much harm to him unless he was forced to stay still.



More troubling were the Nine he couldn't put down.  The Siberian was untouchable, an immovable object, invincible in a way that even Alexandria wasn't.  Even if he were capable of hurting Crawler, he wouldn't want to.  Mannequin, he wasn't sure about.  He knew the crazed tinker had encased himself in a nearly indestructible shell.  As strong as Hookwolf was, he faced that distant possibility that any of these people could pin him down or set him up to be taken out by others.



Who else?  He wracked his brain.  Jack Slash was the brains and leader of the operation.  Not a threat unto himself.  Shatterbird couldn't harm him, he was almost certain.



Bonesaw.  She was the wild card, the most unpredictable element in terms of what she could bring to the table.  So often the case with tinkers.



He strode across the room to the windows and gazed out at the city block surrounding the home base of the Chosen.  Glass was still raining down from the sky, glimmering in the orange-purple light of the setting sun.  Every window in view was broken, empty of glass.  Car windshields, streetlights and signs had all been affected, and the surrounding surfaces of wood, metal and fiberglass all bore the scuffs and gouges of the fragile shrapnel.



Every piece of glass in the room suddenly stood on end, points facing upward.  He gave it a moment of his attention, then turned to the world beyond the window, hoping for some glimpse of his adversaries, a clue about where they were.



``Cricket,'' he called out.  ``You alive?''



He heard a sound, movement, and turned. She was gingerly searching through the carpet of weaponized glass shards for her artificial larynx.  She found it and pressed the cylinder to her throat.  ``Alive.''



``You said something was wrong.  What did you notice?''



``Sound.  The glass was singing.  Still is.''  She pointed at one wall.  Hookwolf followed the line to a building across the street and a little ways to one side.



His ears were ringing, but he doubted that was it.  It would be something subsonic that Cricket noticed with her power, then.



``You come with me, then.  Menja, Stormtiger, I leave it to you to see to my Chosen.  See if Othala is able to help.''



``On it,'' Menja said.  Thin trails of blood ran down from the points where glass splinters had pierced her skin, but the damage hadn't gone any further.  She stooped down and picked up Stormtiger in her arms.



Orders given, Hookwolf drew the majority of his flesh into a condensed point in his `core', felt himself come alive as more metal spilled forth.  Only his eyes remained where they were, set in recessed sockets, behind a screen of shifting blades.  He was half-blind until the movement of the blades hit a rhythm, moving fast enough that they zipped over the surface of his eye at speeds faster than an eyeblink.



He let himself fall from the third floor window and hit the ground in a state that was more liquid than solid.  Blades, spears, hooks and other twisted metal shapes all pooled on the pavement, absorbing the impact.



He pulled himself together, in his favored quadruped form.  Looking up to the window, he created a tall spear from between his `shoulders'.  Cricket leaped out and caught the pole, slid down until she could hop off and land beside him, skidding on the glass covered surface.  She looked annoyed as she looked down at her shoes, raising one foot off the ground to investigate the underside.  Glass had embedded in the soles.



He would have told her to ignore it, but he couldn't speak.  For that matter, neither could she.



Cricket pointed, and he led the way with her following directly behind him.  As he walked, he wasn't moving his limbs quite so much as it might appear at first glance.  Instead, he extended one growth of metal as he retracted another, only generating the illusion.  A hundred new parts growing each second to suggest shifting musculature, a cohesive form, when he was anything but.  Only the core skeleton, the shafts of metal that formed the limbs from the shoulders or hips to his knees,  actually moved without retracting or extending.



Glass rose from the ground to fit together into a window that floated in the air and he smashed through it with one of his forelimbs.  Another barrier appeared, thicker, and he smashed that as well.  The glass began to form into dozens, even hundreds of barriers.  He quickly found one strike wasn't enough to clear the way.



Through the mess of dozens of dirty and wet panes of glass, he saw her.  Shatterbird.  A sand nigger, going by memory and the color of her exposed skin.  The upper half of her head was covered in a helmet of colored glass, and her body was covered with a flowing garment made of tiny glass shards, like scales.



He rose onto two feet, standing straight, and reconfigured his arms.  With spears as big around as telephone poles, he punched through thirty or forty panes of glass all at once, then did the same with his opposite hand.  It was slow progress, as the glass constantly reformed and pieced itself back together a few feet ahead of him, but he was closing in.



She abruptly dropped the barriers and changed tactics.  The majority of the glass in the area formed into one shape, a cone of solid glass, pointing towards the center of the purple-red sky, two and a half stories tall.



Raising one hand, she shot it straight up into the sky above, until it was just a speck.



Hookwolf lunged for her, only to find that the residual glass that remained on the ground was denying him traction.  His metal claws failed to find grip, failed to crack the glass, even with the heavy impacts and his impressive weight.  Closing the distance proved slower than he'd hoped.



The massive spike of glass plummeted from the sky.  He knew it was coming, had kept an eye out for it, and timed a leap to coincide with its descent.



No use.  It veered unerringly for him, speared into him with enough force that it nearly sheared him in half.  Cricket uttered a strangled scream as she got hit by the fallout of glass shards and scraps of metal.



``Stand,'' Shatterbird said.  Her voice held traces of a British accent, and her body language and the crisp enunciation made her sound imperious, upper class.    ``I know you survived.''



Hookwolf struggled to pull himself together.  He used hooks to pull the metal back towards his core, where it could be reabsorbed, recycled.  It didn't take much of his reserve of internal energy to create and move the metal, but it took \emph{some}, and he'd rather not run out.



It was a risk, he knew, but he needed a few moments to pull himself together and rebuild his body.  He let his head and upper chest emerge from the core, taking form in the hollow metal `head' of his canid form.



``What do you people want?'' he asked.



``Person.  Singular.  I am the only member of my group here,'' Shatterbird informed him.



``Arrogant.''



``You can be arrogant when you're strong enough.  You should know, Hookwolf.''



``You here to make trouble?''



She shook her head, her helmet sparkling in the light cast by the setting sun.  ``I'm the Nine's primary recruiter.  I have an eye for people who can thrive among us, and I have brought more than five individuals on board.  I thought long and hard before settling on you.  I am not about to let you turn me down.''



So that was why she hadn't hit the entire city with the blast, shattering the glass and maiming or killing hundreds.  She hadn't wanted to kill any prospective members, wanted to reserve her power for when it would be most dramatic.



``I'm fine where I am.''



``This isn't a request.''



``Is that so?  You going to make me?''  He was nearly restored.  He could fight now if he needed to.



``Yes.  I know who you are, Hookwolf.  I spent some time researching your history.''



``Not that interesting.''



``I beg to differ.  You ally with the Aryan groups.  Run one, but your motivations seem to be different.  I have guesses as to why, but I'd rather you tell me.''



``Tell you?  Why should I?  I think we're done here.''



Shatterbird raised one hand, then frowned, her lips pursing together.  ``Hm.''



Cricket climbed to her feet.  She was bleeding badly where she had exposed skin, and chunks of glass were partially buried in her arms and legs.  There was the quiet rasp of her laughter.



``Pride goeth before the fall,'' Hookwolf said, striding towards his enemy.  ``Seems as though Cricket can use her subsonics to cancel you out.''



``Seems so,'' Shatterbird answered, rapidly backing up to maintain some distance from Hookwolf.



``And here I was thinking you'd won the lottery with powers.  Incredible range, fine control, devastating force, versatility\ldots and all it takes is the right noise and it all falls apart?''



``Guess the men who bought my power should ask for a refund.''



``No.  Not interested in being conned into a game of twenty questions to figure out what you're talking about.  Not giving you a chance to figure a way out.''  He punched one of his massive spears at her, and she threw herself to the ground, rolling beneath the impaling weapon.  As she stood, she drew a gun from the folds of her glittering dress.  She fired between Hookwolf's legs at Cricket, the noise of the shots ringing through the air.



Hookwolf didn't even need to look.  He laughed, ``No.  Afraid my lieutenant is a little too fast for you.''



``Look out,'' Cricket's said from behind him, the artificial sound of her voice detracting from the inflection and urgency.



A tide of glass slammed into him.  Standing on only two limbs, his balance suffered, and he wasn't able to keep from being pushed onto his side.



``Wasn't aiming at her,'' Shatterbird said.  She fired several more shots, simultaneously releasing a shard of glass from her free hand.  Hookwolf turned, saw Cricket clutching her throat.  She'd dodged the bullets, but Shatterbird had controlled the flight of the glass shard she shot at Cricket much in the same way she'd controlled the descent of the massive spike of glass.  It had struck its target.  ``Just needed to break her concentration.''



Cricket collapsed, large quantities of blood spilling through her fingers and around her hands, where they clutched her throat.



``Now it's just you and me,'' Shatterbird said.  She dusted herself off, not giving any concern to the sharp edges of the glass shards that made up her garment.  ``We talk.''



``I think I'll kill you instead,'' Hookwolf growled.



``What's the rush?  In fact, any moment we delay, you have a chance of reinforcements arriving.  Your Stormtiger, your Othala, your Menja, they could all do a little something to assist you.  It's in your advantage for us to delay the fight.''



``Except I'm more than capable of putting you down myself.''



``Perhaps.''



He adjusted his form, dropping to four legs once more.  The aesthetic suffered, but he created two needle-tipped limbs at his shoulders, poised like scorpion's tails.



``Ah, that's much better,'' she said, ``But you're still too attached to conventional forms.  Why have legs at all?''



``They're enough.''  He pounced.  She leaped to one side, and almost glided to a position across the street.  She was using the glass of her costume to levitate herself.



From her new vantage point she told him, ``I did say I had my suspicions about your motivations.  I think I've come to understand you. Jack encourages this, you know.  Understanding our targets, be they recruits or victims.  You learn a lot being with him.  I believe you, Hookwolf, are a born warrior.''



He pounced once more, driving both foreclaws at her and following up with two quick jabs with his needle-tipped limbs.  She dodged all three hits, then swept a carpet of glass beneath him as he pounced quickly after her.  He landed and skidded on the surface like one might with a carpet of marbles, falling onto one side, and she threw a tidal wave of glass shards at him, driving him across the street to distance him once more.



He stopped to draw his head and upper body back into the core.  The wave of glass had come too close to penetrating the head of his form and cutting his flesh.  It was dangerously vulnerable.



A warrior at heart, she'd said.  He'd thought, sometimes, that he was born at the wrong time.  Had he been born in Rome's heyday, the Crusades or any of the great wars, in eras where martial pride and strength were valued, he thought he might have been a great person, a soldier feared on the battlefield.  He would have relished that life.  Here, now?  Even with powers, he wasn't so notable.  People with a tendency for violence and a thirst for blood just didn't thrive.



``What I can't figure out--'' she paused to throw herself up to the top of a four-story building, then raised her voice to be heard on the ground, ``Is what you're doing with these `Chosen' of yours.''



He couldn't speak to answer her, and only climbed the building's face.  He was three-quarters of the way up when she leaped down, soaring toward the sidewalk on the opposite side of the street.  Always keeping her distance.



A gale caught her, and her lateral movement stopped.  As wind twisted around her, she was driven down into the street, hard.



Hookwolf would have laughed if he could.  He looked at his headquarters and saw Stormtiger crouching by the front door, clutching a blood-soaked rag to his throat.  Stormtiger wouldn't interfere where it counted, but he \emph{would} give Hookwolf the opportunity to confront his opponent.  He adjusted his position and fell to the street next to Shatterbird.  She held one leg while laying on her back.  She'd fallen badly.



Stalking towards her, he heard she was still talking, ``You call them Fenrir's Chosen.  I'm a scholar, believe it or not.  I know Fenrir was one of the beasts that brings about Ragnar\"{o}k, the death of the gods.  Fenrir was the beast who slew Odin, Allfather, king of the gods.  Fenrir was a \emph{wolf}.  Too coincidental for that to be an accident on your part.''



He stirred the blades that made up his form, pushing himself to be bigger, more dangerous as he closed the distance.



``A sword age, an axe age.  A wind age, a wolf age.  A world where none have mercy.  I can believe this is your goal, your ultimate objective.  Do you crave to reduce this city to darkness, blood and ash, so that only the strong will survive?  Do you tell your followers that it is only the \emph{pure} will rise to the top in the new world order?''



He set one clawed foot down on her.  He could feel some blades on the underside of his foot bite into her flesh.  She didn't fight him or resist.



``Join us,'' she said, her voice strained.



He formed a head and mouth.  His voice echoed from within his metal skull, ``You describe me as a warrior, why would I join petty killers?''



She shifted her position, huffing out sentences between gasps of pain.  ``Only a matter of scale.   Need more like you in our number.  Frontline combatants.  Capable of carving murder through the ranks of the innocent.  Through our enemies.  We could be great warriors.''



``Not interested.''



``We could create your Ragnar\"{o}k more than any number of Chosen.''



``They are my people.  I won't turn my back on them.''



``Then kill me.''  A thin smile crossed her face, though her expression was drawn with pain.  When she spoke, it was in more short sentences. ``But know that your dream is over.  Unless you come with us.  Once nominated you'll be tested.  By others, whether willing or not.  I have left notes.  Urging them to kill your soldiers.  To raze any place you might call home.  To bestow fates worse than death.''



He raised his claw from her.  She was bleeding from wounds in her stomach and pelvis.



He'd had a hard enough time killing this one.  If the other seven arrived?  No, he wouldn't be able to stop them alone, and his lieutenants were not strong enough to hold them off.



``And you won't rescind these orders and requests?''



``I will.  \emph{If} you join.  You give me your word, I leave.  You will be tested.  Your people left alone.  When the test is done you're\ldots either dead or one of us.''



``What is it \emph{you} want?''



``Make history.  Names in books.  Taught to schoolchildren for years.  Centuries.  Our goals\ldots'' she winced, pressed one hand to her stomach, ``Coincide.''



He pondered for a few moments.  Could they escape?  No, you didn't escape the Nine.  He'd already considered fighting, but that option was out.



There was a possibility he could lay a trap for them.  Or buy time for his people to escape.



``Fine.''



Another thin smile crossed her face.  She used her power to raise herself to a standing position, her toes only barely touching the ground.  ``So loyal.''



``But I won't forget what you've already done.  If you survive, I will wait for the right time and place, and I will kill you.  One day.''



``Already thinking like\ldots one of us.  Rest assured.  I will survive.''



Glass drifted towards her to fill the injuries, cracking in the right spots so each fragment fit the wounds perfectly.  The smallest particles of glass, a fine cloud of dust, flowed forth to fill the gaps.



Then she rose into the sky.  Hookwolf signaled for Stormtiger to hold his fire.



He wasn't going to accept this.  They'd insulted him, hurt his people.  They wanted to subvert his mission and twist it to their own ends?  No.



His face twisted into a scowl as he looked over the glass-strewn street, and at Cricket's prone form.  He'd told Shatterbird he'd kill her sometime in the future, had hopefully led her to expect something further down the line.



No, he would go through the motions of their `test', even join them for the short-term.  But he'd kill them sooner than later.  Before they left the city.



He looked at his people, saw Othala hurrying over to Cricket's side to grant the young woman regenerating abilities.  Rune was hurt, the right side of her face torn up, healed only enough to close the cuts and stop the worst of the bleeding.  Probably Othala.  Everyone else was injured to some degree, many gravely.



He'd need help from elsewhere.





