





If each of the tens of trillions of universes were like pictures, then they were organized into a mosaic, constantly rearranging itself and shuffling.  Taken in as a whole, it was a muddle.  Depending on how it shuffled, sometimes patterns emerged.  A predominant color, perhaps, or lots of scenes that were blurs of motion and activity.



But there was more to it.  There were faint sounds, for one thing, and they weren't just two-dimensional.  Just the opposite – they were each a fully realized world, and each was continuous, like a slideshow or film reel that extended vast distances forward and backward from any of the scenes of focus.  Things got even more complicated when each of the slideshow reels forked out and branched as they moved further away.  The only thing stopping them were the terminus points.  The first terminus wasn't complicated.  The now, the present.  It moved inexorably, steadily forward, consuming the individual realities as they ceased to be the \emph{future} and became the \emph{now}.



The other terminus was somewhat more ominous.  Every branch ended at some point, some sooner than others.



Dinah Alcott knew that those branches were ones where she had died.  Right now, there were a lot of them, more coming into view with every passing second.  Almost all of the images in the mosaic were either black or crimson.  Either the lights were on and everything was covered in blood, or they were off, and she was effectively blind.



She concentrated, and the mosaic organized into two portions, one slightly larger than the other.  In one half, that death-terminus came very soon.  In the other, it was some distance off.  She judged the size of the individual parts, and the number snapped into her head.



\emph{43.03485192746307955659 percent chance she would die in the next thirty minutes}.  The chance was steadily ticking upward with each passing second, with possible realities becoming impossible and fading from her view, or being replaced with other possibilities, effectively shifting over to the other side.



Anxiety crept up on her.  She wanted her `candy', to take the edge off, to help clarify her thoughts.



She knocked on the door to her room.  She heard Coil say something on the other side and tested the knob.  Finding it unlocked, she stepped through.



Coil sat at his desk, on the phone.  She didn't want to talk to him, but she wanted to die less.



``It's unfortunate,'' Coil was saying.  ``Step up recon, call in a secondary team to ensure twenty-four seven surveillance.  We'll want a replacement for our Leah the moment they start recruiting again.  Yes.  Good.  Let me know.''



He hung up.



``Coil?''



``What is it, pet?''



``Forty-four point two zero three eight three percent chance I die in the next half-hour.''



He stood from his desk.  ``How?''



``Blood or darkness.  Don't know.''



``The chance \emph{I} die in the next thirty minutes?''



She thought, and felt the mosaic shift into a new configuration.  Coil's face predominated each tiny scene, active, speaking and alive in some, unmoving or dead in the others. ``Forty two point seven zero nine percent for the worlds where I don't die.  Don't know about the worlds where I'd die first.''



``And, say, Mr. Pitter?  The chance he dies?''



``Forty point-''  She stopped as Coil raised a hand.



``So whatever it is, it happens here, and involves everyone here.  Chance of survival if we leave?''



``Ten point six six four-''



``No.  Chance the average person in the city lives if we leave?''



``Ninety-nine point-''



``So we're targets.  It's not an attack on the city.  If we mobilize the squads?  To one decimal place?''



``Forty-eight point one percent chance I survive, forty-nine point nine percent chance you survive.''



``No difference.  Worse if anything,'' he said.  She nodded, and he rubbed his chin, thinking.



Time was running out.  She fidgeted.



``I need some candy, please.''



``No, pet,'' Coil said, ``I need you focused.  What-''



She interrupted him, which always she tried to avoid doing, but she was feeling desperate.  ``Please.  I've been using my power a lot.  I'm going to get a bad headache, and then I won't be useful to you.''



``No,'' he said, with more ferocity than she had expected.  ``Pitter isn't here to administer it, and won't be until this situation is over.  Listen.  Chance that we survive Crawler's attack if my soldiers use the laser attachments I've provided?  The purple beams?''



Crawler?  It took her a second to get her mental footing.  Coil was using his power.  She wasn't sure how it worked, but she could always tell when he was doing it because the numbers always started changing all at once, and he knew things he couldn't.  He'd know about things and numbers she might have told him, except she didn't remember telling him.



``Thirty Nine point one-''



``If I deploy the Travelers that are on site at the moment?''



``Thirty point-''



He pushed his monitor off his desk in a fit of anger.  It crashed to the floor, pieces of screen rolling and sliding onto the rug at one end of the room.



Striding around the desk, he seized her by the arm and pulled her out of his office.



``Candy.  Please,'' she said, whispering.



``No.''



Gripping her wrist so hard it hurt, he drew her into the main area of his underground complex.



``Get battle ready!'' Coil shouted.  It was so out of character for him to shout.  ``Threat incoming!''



The soldiers that were at ease in the lower area of the base jumped to action, grabbing weapons and protective wear.



It wasn't going to make a difference.  The numbers weren't changing enough.  But he was already upset, so she didn't tell him that.



Trickster, Oliver and Sundancer appeared, running along the metal catwalk.  Sundancer had her mask off, and her permed blond hair was damp against her scalp with sweat.  Oliver was in casual clothing, like Trickster.  He was good looking, his features chiseled.  Athletically built.  Trickster wasn't.  He had a hook nose and long hair that didn't suit him, but she knew he was smart, and she would have guessed it even if she didn't know, just going by the way he looked at stuff.



``What's going on?'' Trickster asked.



``My pet has graciously informed us that Crawler of the Slaughterhouse Nine is less than thirty minutes away from entering this complex and murdering us all.  Suggestions outside of the obvious would be appreciated.''



``Trickster and I could go and try to stop him,'' Sundancer suggested.



``\emph{Outside of the obvious}, Sundancer.  I've asked my pet.  You try that and we're all \emph{more} likely to die.''



``Why?''



``He's a regenerator,'' Coil answered, sounding irritated at having to explain, ``And he regenerates exceedingly quickly.  More to the point, he has the added advantage that any part that grows back is stronger than it was before, typically with extra features, growths and increased durability to render him more resistant to whatever hurt him or give him other capabilities.  These adjustments are not only permanent\emph{, }but he's been working on it for some time.''



Trickster added, ``I read up on these guys after you mentioned them the other night.  Crawler eventually becomes immune to whatever was hurting him, and he's that much less human, afterward.  He \emph{wants} to get hurt, wants to further his transformation, like a crazed masochist or someone with a death wish.  Throws himself into suicidal situations and then comes out stronger.  Which may be why he's here.  The soldiers?''



Coil shook his head, ``He's immune to conventional ammunition and explosives, and most likely to most \emph{unconventional} forms of ammunition and explosives as well.  The laser attachments might have some small effect, but not enough to draw him here.''



``Which makes me wonder all of a sudden how he found us,'' Trickster added.



Coil shook his head, ``One thing at a time.  If he is here because he's seeking someone who could harm him, the only individuals on site who would be capable are Sundancer and your Noelle.''



That gave the three teenagers pause.



``Noelle?  But who even knows about Noelle, except-''



Coil raised his hand to silence Trickster.  ``Pet, the chance that Crawler would seek out Noelle first, given the opportunity?''



She felt the images filter out until she was looking at a pattern of scenarios.  The vague shape of the hulking figure, the open vault door.  The images snapped into two groups, one vastly larger than the other.



``Ninety three point four percent.''



``\emph{Shit},'' Trickster swore.  ``That's why he's here.  Just like Leviathan, Crawler's coming after her?''



``I find every piece of evidence we gather only supports our working theory on your teammate,'' Coil said.  He turned to Dinah, ``The chance of survival if we were to give him what he wanted?  Give him access to Noelle?''



``Hey, no,'' Trickster said.



``Eighty-one point nine percent chance we survive the next hour-''



``A start,'' Coil noted.



Something about the image bothered her.  She pushed forward, seeing the possible realities that unfolded after that.  Very, very few extended any meaningful distance into the future.



``Six percent chance we survive the next \emph{five} hours.''



Coil stopped, then sighed.  ``Thank you, pet, for clarifying that.''



She nodded.



``Awesome,'' Trickster responded, his voice thick with sarcasm.  With a more serious tone and expression, he said, ``Let's not give him access to Noelle.  Agreed?''



``Agreed,'' Coil conceded.  ``Any further ideas?''



\emph{Time's running out}.  She looked at the numbers for herself, even though she felt the initial throbbing pains at the base of her skull that foretold the encroaching headaches.  \emph{53.8 percent chance I die in the next thirty minutes}.



``Pet,'' Coil said.



What she didn't get from his tone, she grasped from the vague images she saw of her most immediate possible futures.



``No,'' she pleaded, before he'd even told her what he wanted.



``It's necessary.  I want you to look at a future where we survived, and I want you to tell us what happened.''



``No.  Please,'' she begged.



``\emph{Now}, pet.''



``Why is she so against this?'' Trickster asked.



``Headaches,'' Dinah answered, pressing her hands to her head,  ``It breaks my power.  It takes days, sometimes weeks before everything is sorted out and working again.  Headaches the entire time, until everything is sorted out, worse headaches if I try to get numbers in the meantime.  Have to be careful, can't muddle things up.  Can't lie about the numbers, can't look at what happens, or it just becomes chaos.  Safer to keep a distance, to make and follow rules.  Safer to just ask the questions and let things fall into place.''



``We don't have time to play twenty questions,'' Coil said.  ``Would you rather die?''



Would she?  She wasn't sure.  Death was bad, but at least then she'd go on to the afterlife.  To heaven, she hoped.  Finding an answer and surviving would mean days and weeks of absolute hell, of constant pain and not being able to use her power.



``Pet,'' Coil said, when she didn't give him an immediate response, ``Do it \emph{now}, or you won't get any more candy for a long while.''



She could see those futures unfolding.  He \emph{would}.  She could see the pain and the sickness she experienced, the full brunt of her power without her candy to take the edges off, complete with all of the details she didn't want.  Worst of all were the feedback loops.  To go through withdrawal from the drugs, from her `candy', while simultaneously being able to see and experience echoes of the future moments where she was suffering much the same way?  It was a massive increase in the pain and being sick and mood swings and insomnia and feeling numb and skin-crawling hallucinations.  There was no limit to these echoes, the feedback from her futures.  It would never kill her, knock her out or put her in a coma, no matter how much she might want it to.



She had come close to experiencing it once, early on in her captivity.  Never again.  She would obey Coil in everything he asked for before she risked that happening again.



``Okay,'' she murmured.  She picked out one of the paths where they survived.  Even looking too closely at it made her head throb, like it was in a massive vise and someone had just cranked it a fraction tighter.  Some of the possible worlds around the fringes of her consciousness disintegrated into a mess of disordered scenes as she pushed forward.  The scenes and images of the less possible worlds flew around her mind like razor-sharp leaves in a gale, cutting at everything they touched.  ``It hurts.''



``Now, pet.  As quickly as you can.''



He didn't know.  It was something else, like trying to will herself to stick a hot poker in her body, in her \emph{brain,} knowing it would remain there and burn her for weeks before it cooled.



But she did it, because as much as it would hurt, it would hurt more if she didn't get her candy.  If Crawler got his hands on her, it wouldn't hurt at all after those first few moments of pain, but that was bad too.  It meant dying.



She focused hard on that scene, taking it from an image small and vague enough that it could have fit on the end of a pencil to something full size.  Her head exploded with pain.  She caught fragmentary images as she felt herself double over and heave the contents of her stomach onto the metal catwalk and Sundancer's legs and feet.



Sundancer could have yelled, but she didn't.  Instead, she fell to her knees and grabbed Dinah by the shoulders to steady her.  It was just in time, because Dinah felt fireworks erupt in her brain, felt her body go spastic.  Too much, too fast.  The image was overly sharp and detailed, overwhelming her senses, shredding all sense of time and present.



It was long moments before she could even piece together what the others were saying and doing.  She was lying down, her head on Sundancer's lap, a cold cloth against her forehead.  Oliver leaned next to her, holding a bowl of cold water.



``-running out of time!'' Trickster shouted.  Coil stood just behind Trickster, arms folded, staring out over the railing, at his underground base.



``Give her a moment,'' Sundancer said.  ``Whatever that was, it just knocked the poor kid out.''



``That deadline she gave us?  It's \emph{here}.  \emph{Now}.''



``I know, but pressuring her won't help anything.''



A smell hit her.  Like the bitterest black chocolate in the world and overly strong coffee, the odor so thick on the air that she could taste it.  With her already upset stomach, it made her want to retch.



``Smells bad,'' she said.  ``Make the smell go away.''



``She's conscious.  Is this smell a clue?'' Trickster turned.



``No.  It's a symptom,'' Coil answered him, not turning to look at her or them.  ``She may be dizzy, dazed, or she may rub or scratch at herself until she fully recovers.  Don't let her scratch her corneas or rub herself until she bleeds.''



Dinah tried to recall what she'd seen.  ``Darkness.''



``You mentioned that earlier, pet.''



``We were in the dark, and it smelled like meat.  It smelled like sweat, too.  And we were all pressed in close together.''



``\emph{Where}?'' Coil asked.



``There was a metal door in front of us.  Big.  The vault door downstairs.''



``Noelle's room,'' Trickster said, an instant before Dinah put the pieces together.



``How many of us, pet?''



``Everyone here was there,'' she looked towards the soldiers.



``Is \emph{she} in there?''



``She was.  Yes.''



Coil turned and swept her up in his arms.  Her skin crawled at the contact of her body against his.  She didn't say or do anything about it, in part because she wasn't able, too sick, hurting too much.  The other reason was because she had seen the numbers shift each time she flinched away from his touch or made her disgust known.  Little differences.  He was angrier with her, more curt, if she pulled way, if she complained about it.



There was safety in the numbers, in following the rules she set on herself.  It kept her power in order, it ensured Coil was tolerant with her, and it meant she didn't have to go without her candy for even a short time.



Coil took the stairs two at a time as he descended to the ground floor, Trickster, Oliver and Sundancer hurrying after him.



``You,'' Coil called out, not even bothering to recall the employee's name, ``The vault door.  Open it.  Squad leaders, organize your groups!''



There was a faint crash in the distance, and a vibration rippled through the complex.



``Pet, the chance that Crawler kills us, now that we've undertaken this route?''



``I don't.  I can't.''  Her head hurt so much.



``\emph{Try},'' and in his hard tone, she heard the unspoken threat of having her candy taken away.



She did.  The scenes had no order to them.  They were all jumbled, and trying to pull some semblance of order and sense into them was like thrusting her hands into fire and razor blades, thrusting her \emph{mind} into fire and razor blades.  A long groan of pain was drawn from her throat, and the strength went out of her body.



``You're killing her!'' Sundancer gasped.



``No,'' Coil said, as if from a place far away.  ``I've had her use her power to check.  This may be miserable for her, but she can't die from it.''



Coil touching her, that overpowering phantom smell, the fear, the nausea\ldots



``I need to barf.''



Coil set her down and held her by the wrists as she leaned forward to cough up mouthfuls of bile.  Her stomach was already empty of food.



``The number, pet?''



Sundancer bent down to hold her, so her shoulders weren't being twisted with her arms held behind her by Coil.



``Three point one percent,'' Dinah gasped out.



``Reassuring,'' Coil said.  The vault door opened before them.  ``Trickster?  Would you announce our imminent arrival to Noelle?''



``Yeah,'' Trickster sighed.  ``Fuck.  I hate to do this, but can I get a number?''



``Trickster!'' Sundancer admonished him, sounding horrified, ``You can see how much pain it's causing her.''



``It's important.  Kid, what's the chance that \emph{Noelle} kills us?''



There was another series of crashes, closer.



Dinah shook her head, ``Please.  I just want to put everything back together.  Every time I use my power, it all falls apart and it \emph{hurts}.''



``Pet, it's the last question we'll ask you tonight.  I promise,'' Coil said.



So she did.  She reached for the number.  \emph{It can't kill me.  It doesn't do permanent damage.  It just hurts.  It's my brain telling me my power shouldn't be used to find answers like that}.



The words she used to convince herself did little to soften the pain that came with digging for a number once more.  She screamed, and tears flowed down her face as she sank into Sundancer's arms, screwing her eyes shut.



``Nine point eight percent,'' she managed.  Was she being carried?  They were venturing inside, past the first of the two heavy vault doors.  How much time had just passed?  Where was Trickster?



``That's good information to have, pet,'' Coil said, from somewhere near her.  ``Squad leaders.  As you gather inside the containment room, I want you organizing your troops into ranks, your backs to the door.  Weapons need to be locked, loaded and ready to fire.  Be sure to equip the laser attachments and battery packs.  Don't venture any further than ten paces inside.''



There were affirmative responses.  Dinah could hear guns cocking.



Another crash, the closest yet.  The sound of rubble and concrete falling echoed through the underground complex.



``He's here,'' Coil said.  ``Last people inside, \emph{hurry}.  Close the first door.''



Dinah opened her eyes.  They were in a concrete room with steel girders at set intervals, as if forming a cage against the inside of the room.  It smelled like meat that had gone bad.



The second vault door slowly swung closed as the last few stragglers slipped through the gap.  Employees, technicians, people in suits, some soldiers.  They packed in close at the end of the room closest to the door, their bodies pressing against her.  Three fifths of the chamber were left unoccupied.



And on the other side of the room – darkness.  Trickster was emerging.



``How is she?''  Coil asked.



``Scared.  Hungry.  She said she didn't get her meal tonight,'' Trickster answered, his voice quiet.



Coil folded his arms.  ``She did.  I personally observed the delivery.  I suspect she's needing more food as of late.  Unfortunate we find this out \emph{now}.''



``She asked me to turn out the lights on this end of her room.  Said it would be easier if she can't see us.''



``Do it,'' Coil ordered.  He strode over to one of his squad captains and spoke in the man's ear.  Dinah thought she might have overheard something about night vision goggles.  She closed her eyes, as if it could help shut out the pain that continued to tear through her skull.



The pink of the light shining through her eyelids turned to black as the lights went out.



``I'm sorry,'' A girl's voice whispered in Dinah's ear.  Sundancer?



Dinah tried to answer, but her voice came out in a croak.



``I'd help you if I could, but I can't, you understand?'' Sundancer whispered to her.  She had her arms around Dinah.  She smelled like barf, but that was Dinah's fault.  ``It's not just that my friends and I are in a bad spot, or having to help Noelle, or even that I don't think I could save you on my own\ldots  We made a promise to each other, when everything began.  Fuck, it sounds so stupid, sounds so lame, when I say it like that.''



There was a crash nearby, the sound of metal on metal.



Then a massive impact against the vault door made the room shudder.



Sundancer kept talking, as if oblivious to the ongoing attack.  ``When you've been through hell and back again with a group of people, when you've all lost everything, and you collectively stand to lose \emph{more}?  I- I don't even know what I'm saying.  Maybe there's no justification for letting you go through what you are.  I just\ldots they're all I've got.  I'm sorry.''



Dinah reached up and fumbled around until she found Sundancer's hand.  She didn't have a response, couldn't speak if she'd been able to think of what to say.  She just held the hand tight.



A series of hits collided with the metal door.  A roar rattled through the air, painfully loud despite the muffling effect of the intervening wall.  It was a roar heavy with frustration and anger.



There was the sound of guns cocking.  She almost missed it in the midst of the steady, relentless crashes that came from the metal door.



``I'm so hungry,'' a girl's voice echoed through the chamber.  \emph{She's close}.



``I know, Noelle,'' Trickster answered.  ``Just a little while.  Let's go back to the other side, away from these people.''



Noelle sounded like someone who was very, very tired.  ``Can't wait.  Can't wait at all these days.  I can \emph{smell} them.''



\emph{She wants food as badly as I want my `candy}`, Dinah thought.  \emph{The difference is that she can and will take what she wants, even if it means eating one of us.  I don't have that power.}



God, her head hurt.  Worse, she knew this was the calm before the storm.  Her head would hurt more with every passing hour until she wanted to die.



``You can hold on,'' Trickster said, his voice gentle.  ``You don't want to come any closer than that.  You know what your power does.  None of us want that.''



``No.''



``And these guys, as good as they are, I can't be positive that one of them won't shoot you in a moment of panic.  We don't want that either.''



``I'd live.  Don't want to, but I'd live.''



``You would.  But would I?  Would Oliver and Marissa, if you went berserk?  They're in here too.''



Sundancer spoke up, calling out, ``Remember the promise we made together.''



Noelle didn't reply.  The silence lingered, punctuated by the heavy blows on the metal door, echoing through the concrete chamber.



``Come on, Noelle.  Let's go back, before you or someone else here does something they'll regret,'' Trickster urged.



The banging continued.



``Come with me, Krouse?  We can talk alone?''



``That sounds good,'' Trickster said.



Dinah felt the tension in the room ease.  The pain in her skull didn't get any better.  She set about the tedious task of trying to reorganize the images in her head.  Building a house of cards in an unpredictable wind.  Every time the numbers changed, what she'd started to sort out fell apart.



She'd have to wait until a period of calm before she made any real headway.  The passage of time would help as well.  Then it wouldn't be so painful to use her ability.



She got caught up in the painstaking operation, and it was some time before she realized the banging had stopped.  Still, the gathered people in the room waited.  Just in case Crawler was bluffing them, waiting until they opened the door.



Long minutes passed before Coil gave the order.



Dinah was blind.  Her power too fragile and painful to use, so she couldn't see the future that awaited them outside the door.  Her heart pounded in her throat as the door was opened.  The first squads moved out, fanning through the complex to find if Crawler was lurking in some corner of the underground base.  They returned and gave the all-clear.



Emerging from the gloom, she squinted in the face of the fluorescent lights.  Claw marks gouged the outside of the solid steel of the vault door, each at least half a foot deep.  The catwalk had been torn down at one side of the complex, and innumerable boxes of weapons and supplies had been crushed or scattered across the floor.



``Candy?'' she asked.  ``My head hurts.''



``You can have your candy, pet.  Go to your room, I'll call Pitter in and send him to you.''



With her armed escort, she headed to her room.  She collapsed gratefully on her bed.



She knew she'd regret it, but she used her power.  She had to know.  It would be one more use, to hold her over, and she would stop using her power for the next few days, at least.  Weeks, if Coil let her.



She clutched her covers and bit her pillow as her head erupted with pain.  More than half of the groundwork she'd so carefully laid in place over the past hour fell apart as she pulled the scenes into two groups.  Minutes passed before she had her number.



\emph{31.6\%}.



More than four percent higher than it had been yesterday.



Thirty-one point six percent chance she'd get to go home someday.





