





A teenager with a red streak dyed into her dark hair strode down the street in rubber boots.  Three hours past curfew, alone.



She drew a smartphone from the pocket of her jacket, then set to untangling the earbuds.  How did the damned things always get so knotted together?  They were like Christmas lights.  Not that she'd ever untangled Christmas lights, but she'd heard how Christmas lights got tangled.



Popping the foam-covered buds into her ears, she began thumbing through the music as she walked.



\emph{J'adore-}



\emph{Sweet Honey-}



\emph{Love me, love me, you know you wanna love me\ldots}\emph{Love me, love me, you know you wanna love me\ldots}



Her head nodded in time with the beat, and she slipped the phone into her pocket.



She supposed she could have bought something to coil up the cord of the earbuds, or replaced the music playlist instead of deleting everything that didn't appeal.  It wasn't like she didn't have money.  It was an option.  What stopped her was the fact that she had a pattern going.  Everything she owned and everything she used day-to-day was stolen.  The shirt on her back, her shoes, the music, her laptop.  She kind of wanted to see how far she could get before she caved and actually bought something.



Love me, you?\emph{Love me, true?}



Her boots splashed as she danced a little circle, murmuring the words.  The light drizzle had wet her hair, and she pushed it back out of her face, stretched her arms out and let the raindrops fall against her closed eyelids.



It wasn't as though she was in a rush.



She'd walked long enough for six songs to start and finish before someone stopped her.



``Miss.  Miss!''  He was barely audible over her music.



She turned and saw a man in military gear, forty-something, his face heavily lined.  He wasn't wearing a helmet, he had a short buzz cut, a bit of scruff on his cheeks and chin, and his face was beaded with droplets of water.  She pulled out her earbuds.



\emph{Crazed, kooky, cracked, crazy, }\emph{Nutty, barmy, mad for me\ldots}



The crooning sounded artificial coming from the earbuds that dangled from her hand, nasal.



``What's up?''



``Are you okay?''



``I'm \emph{excellent}.''



``There's a curfew during the state of emergency.  I don't want to scare you too badly, miss, but there're rape gangs, murderers and human traffickers on the street.  All people who would prey on a pretty young woman.''



``You think I'm pretty?'' She smiled, stepping closer.



``I have a daughter about your age,'' he replied, smiling tightly.



``That doesn't answer my question.  Do you think I'm pretty?''  She stepped even closer, ran her finger down his chest.



``Yes, but-'' he paused, gripping both sides of her jacket.  He pulled the jacket together, then did up her zipper all the way to the top, around the heavy box that dangled around her neck.  ``That's all the more reason for you to be careful, understand?  Do you have a home or a shelter you're staying at?''



She didn't reply.  Her brows knit together and she undid her jacket and stepped away from him.



He went on, ``I can give you directions to the nearest shelter if you want. It's new, just a little ways up Lord street here.  There may be space.''



``I'm staying with some people.''



``Do you need directions?''



She didn't reply.  She studied him instead.



``If you're willing to wait, I can give you a ride when I'm done here.  I'll get relieved in five or ten minutes, but we could talk in the meantime.  You can sit in my jeep, and you'll be dry.''



She hesitated.  ``Fine.''



The man led her back to his jeep.  She sat in the passenger seat while he stood outside, his eyes on the surroundings, occasionally exchanging words with the person or people on the other end of his walkie-talkie.



After a few minutes, he climbed into the driver's seat.  ``The men who were supposed to take over the watch are late.  Something about fires downtown.''



She nodded.



\emph{Crazed, kooky, cracked, crazy,}
Mental, dotty, whacked, loopy\ldots



``Do you mind turning off your music?''



``I like it,'' she said.  ``I hate silence.''



``Well, I'm not about to deny someone their coping mechanisms.  Where do you live, or where \emph{did} you live, before the attack?''



``Out of town.''



He raised one eyebrow, but he kept looking out the windows for possible trouble.  He put the key in the ignition and started the car so he could use the windshield wipers.  ``Sounds like there's a story there.  People don't just come into town at a time like this, and if you were just visiting, you would have evacuated already.''



``Oh, we're visiting \emph{because} it's a time like this,'' she smiled.



``Thrill seeking?'' his voice hardened.  ``That's not only stupid, it's disrespectful.''



``The people I'm staying with?  They're the Slaughterhouse Nine.  I'm one of them.''



``That's not funny.''  His voice went hard, any gentleness gone.



``It's really not,'' she agreed with a smile.



He went for his gun, but he didn't get that far.  She closed her eyes for a moment, listened for the music that came from his mind and body.  The jangling, dissonant noise of alarm, the throbbing percussion of mortal fear, every part of his body shifting into fight or flight mode.  The underlying notes spoke to his personality.  His love of his family, his fear that he was about to leave them behind, anger towards her, a momentary anxiety that he was overreacting.  She grasped this in the fraction of a second.



Reaching for that mortal fear, she \emph{wrenched it}.  When that wasn't quite enough, she pulled at it and twisted it until everything else was squeezed into the far edges.



He screamed, throwing himself as far away from her as he could get, his weapon falling between the seats.



Crazed, kooky, cracked, crazy,\emph{Nutty, screwy, mentally diseased\ldots}She twisted other parts of his emotional makeup until he was compliant, adrift in apathy, obedient.  ``Stay.''



He stopped retreating.  He was still breathing hard from his momentary panic, but that would pass.



She leaned towards him and ran her hand along the top of his head.  It was like rubbing a toothbrush, spraying minuscule bits of water onto the wheel and dashboard.



``Good.''



He stared at her.  There was fear in the look, and she didn't have the heart to erase all of it.  A little was good.



``I want to drive.  Switch seats with me.''



He nodded dumbly and climbed out of the jeep.  She made her way over to the driver's seat, then waited for him to climb in before she peeled out.



The jeep cut through the shallow water that covered the roads.  Others had noticed her leaving, she knew, and were following in their own vehicle.  She could sense them, each a  fingerprint of emotions in deeply individual configurations.  The mix of personal pride and confidence that she sensed in them suggested they were military.  The soldiers that had been taking over for this guy?



Not much time to do it.  She searched through the feelings of her passenger, found the networks of brotherly love, trust, camaraderie, and adjusted each until the music was one of tension, suspicion, paranoia.  Then she set his fight or flight reflexes into high gear.



``Get the gun.''



He fished for it between the seats, picked it up.



Then he pointed the gun at her.



``No, stop,'' she said.  \emph{Too unspecific.  Fuck.  Still need to work on that.  }She hit him with as much doubt and indecision as she could manage to keep him from shooting her.  Then she stalled all of the `music' that flowed to and from that one point in the very front of his brain.  She knew the music was her way of understanding and interpreting the biological processes that drove people's emotions.  By listening for it, she knew what they felt, knew what the emotions were tied to, vaguely.



There would only be one thing in his short-term memory that was that important right now.  Her.  With that link severed, he would now feel nothing towards her, couldn't summon up any self-preservation, anger or hatred.  Another tweak, redirecting the flow of emotion from his family to her, and he would feel an extreme aversion to the idea of shooting her, wouldn't be able to shoot her any more than he could his own daughter.



He pulled the gun away, dropped it into his lap.  He crumpled over, his hands to his head, then moaned, ``No.''



She was close to her destination.  She pulled the jeep to a stop and hopped out, the other jeep pulling up just a ten or so yards away.  Two soldiers got out.



``Hey!'' someone shouted at her.



She turned her back to them, slipping her ear buds in.  The music had looped back to the first track.  She got her phone out and skipped forward a few times, pausing to delete one song.  She sang along, ``Love me, love me, you know you wanna love me\ldots''



``Hey!''



She could sense her passenger climbing out of the jeep, hear the garbled murmurs of warning, questions.  There was a burst of fear from all three, then the sound of multiple guns firing.  She smiled.  The authorities would have a hell of a time figuring out what happened there.



She'd had her doubts about coming to Brockton Bay.  It had been a turn off to know that areas lacked power, that still more areas lacked working plumbing.  But Burnscar and Bonesaw had both been excited to come, and Jack Slash had bent to Bonesaw's wishes, pushing for the group to come this way.  Crawler, Mannequin and Siberian had seemed fairly indifferent.  Not that Crawler or Mannequin showed much emotion.  She'd thought she had an ally in Shatterbird, at least, but the woman hated her, and the uptight bitch had gone along with the plans to visit Brockton Bay just to ruin her day.



But it was \emph{interesting}, she had to admit.  The landscape of people here was so different.  So many people here were so insecure, so worried.  Most were on the brink of some kind of emotional breakdown, needing just one event, one piece of bad news before they broke down completely.  Others had already been broken, or they'd turned vicious and started preying on their fellows, seeking out vengeance on those who had wronged them in a past life.  In their pre-Endbringer life.



People here were so deliciously fucked up.



This kind of situation, ordinary citizens were doing things they'd never even have considered before.  Stealing, hurting their neighbors, bartering things they once considered precious for clothing, food, toilet paper and other essentials.  Emotions were raw, far closer to the surface, easier to manipulate.



Her music cut off.  She checked the phone.  An alert on the screen notified her that the battery was dying.



She swore.  No more time to waste.  She dialed a number, but didn't hold the phone up to her ear.  Good.  Now she had fifteen minutes.



She reached out and started feeling for the outliers.  The emotional fingerprints that stood out from the rest.



The other seven members of the Nine were out there.  Not hard to find.  One or two were interacting with some other outliers.  The most fucked up people in this fucked up city.  She'd studied each of these unknown outliers over the course of a week, watching their emotions shift as they went out about their lives, sometimes visiting the areas they tended to hang around, to get a sense of their environments.  Slowly, she'd pieced them together, created profiles, discerned which ones had powers and described them to the other members of the Slaughterhouse Nine.  Each had made their picks:



The buried girl.  The arrogant geek.  The dog lover.  The daydreamer.  The warlord.  The scaredy cat.  The broken assassin.  The crusader.



And all \emph{she} wanted was a few minutes to pay a visit to hers.  She didn't have to name \emph{that} one.  He was familiar enough.  She smiled.



Two men sat on the steps outside the building.  She knew immediately that they were soldiers, but they weren't official.  They wore black, and they wore body armor that she hadn't seen before.



``No,'' she stopped them from reaching from their guns with a mixture of doubt, apathy and anxiety.  Complementing her words with a heavy surge of depression, guilt and self loathing, she ordered them, ``Kill yourselves.''



It wasn't immediate, but their willpower wasn't enough to stave off some of the strongest and most agonizing emotions they would have felt in their lives.  It was quick when their composure cracked, the guns flying to mouth and temple to fire.



She could sense the others inside the building, alarmed at the gunshots, moving toward the front.  Four more soldiers and four others who stayed back.  Not soldiers.



She didn't wait for them to step outside.  She did the same thing she'd done to the guards stationed outside, crushing them with despair, overwhelming them with loathing and paranoia.  It was only slightly faster than it had been here.  \emph{Here}, there had been an enemy for the soldiers to focus their negative energies on, to distract them.  It was surprising how important that could be.



Nearly a minute passed before the fourth gunshot sounded, marking the death of the last soldier here.



She tried the front door and stepped inside.  The inside was nicer than the outside, watertight, heavily reinforced.  A feminine looking teenaged boy with a mop of dark curls stood at the other side of the building.  He had two men and a woman guarding him.



``Jean-paul.  \emph{\c{C}a va?}''



``It's Alec now.  Regent in costume.''



``Alec,'' she smiled.  ``Still sounds French.  I approve, little brother.''



``Cherie,'' he ran his fingers through his hair. ``What the fuck?''



``If we're changing our names, I'm going by Cherish.  I wanted to make an entrance.''



``Man.''



``You'll find others.''



``Fuck,'' he sighed.



She reached for the three people who stood between her and her brother, manipulated their emotions towards Alec.  Filled them with suspicion, paranoia, hate.



They didn't budge.



``Cut it out, Cherie,'' Alec said, ``I'm controlling them.''



``If I remember right, you lose control if they're hit by enough emotion,'' she smiled.  She turned up the intensity.



``If I'm farther away.  Seriously, stop.  It's irritating.''



One of the men fell to his knees.  His hands were clenched at his sides.  Beads of sweat rolled down the faces of the other two, tears appearing in their eyes.



``While I'm doing this, you can't tell them to attack me.''



``Unless I've gotten stronger over the past few years,'' Alec answered.  The man who was still standing reached for a knife and started walking towards Cherish.



She hit the knife wielder with fear and indecision, saw him stop.



For nearly a minute, they engaged in a tug of war over the three subjects.



``Seems we have a stalemate,'' she said, finally.



``Did the dirty old man send you?'' Alec asked.



She shook her head, ``Daddy?  I went my own way.  After a bit.''



``How's he doing?''



``Unfocused.  For the longest time, I thought he was building up to something.  Lots of kids, ensuring they had powers.  Thought he'd try to topple the other gangs and become ruler of organized crime in Montreal.''



``But?''



``But it didn't happen.  Time passed, he never made a push for it.  Guillaume got his power, you know.  Ten or so of us kids, and three of us could control people one way or another.  Four if we count you.  We had what we needed to pull off something huge, and Daddy decided he wanted a celebrity among his girls.  Took us on a road trip to a film set in Vancouver, kidnapped this star, took her back to Montreal.  So petty.''



``Somehow I'm not surprised.''



``Heroes came after us, from both Vancouver and Montreal.  Half of what we had built and earned as the Vasil family just kind of got trampled in the fighting that spilled out from that.  All because Daddy wanted to bone someone famous.  I got fed up, left.''



``So you're on your own.  And he didn't send the others after you?''  Alec moved one of his subject's legs so she would fall to the ground rather than point her gun at the man standing next to her.



``He did.  Guillaume and Nicholas.  Guillaume just has to touch someone and he can sense everything they do for a good while.  Nicholas just wallops you with pants-shitting waves of terror.  Literally thousands of eyes and ears looking for me, can't fight when they do get close to me.''



``Right,'' he said.



``Anyways, it got old \emph{real} fast, them constantly finding me, constantly making me pack up and run somewhere else. Besides, the freedom to do what I wanted and go where I wished kind of lost its appeal when the boredom set in.  I would've done it even if my big brothers weren't coming for me, but I joined the Nine.''



She looked at the multitude of small changes that crossed Alec's expression and smiled.



``Well,'' Alec said, after processing her statement, ``That was dumb.''



``It's \emph{exciting}.  I decided I needed to earn a place on the team, both to scare our brothers away and to add some spice to my routine.  Took out Hatchet Face to do it.''



``I got the info on him a day or so ago, after I heard the Slaughterhouse Nine were in town.  Isn't he immune to powers?  That's pretty much what he does.  Super strong, enhanced toughness, big\ldots and your powers just stop working when he gets close.  Or they go haywire.''



``He \emph{is} immune to powers, but he didn't get close.  See, difference between me and Daddy is that I have \emph{range}.  I can use my power even if I can't see the person I'm using it on.  Through walls, from the building next door.  Hatchet didn't get close enough to me to turn off my power.  He tried, but it works both ways.  I was prepped to run any time my power stopped working, because it told me he'd found my trail or guessed where I was.''



``Ah.  I sort of remember that bit about your power.  The part that sticks in my head is that you don't have long-term benefits.  It wears off, and your targets build immunity pretty quickly.''



Cherie shrugged.



``I'm not the best when it comes to strategy, but I'm thinking\ldots I'm going to win here. Eventually.  You can't run without me getting control over my people and sending them after you, you can't use them to attack me, and if you \emph{stay}, I can try doing this.''



Her arm jerked involuntarily.



``Remember me practicing my power on you when it was new?''



``I remember, little brother,'' she frowned, looking at her arm.  ``Daddy had us all practice on each other.''



``Well, I still remember how to hijack your body, pretty much.  Info that's stored away in whatever corner of my brain makes my power work.  I'm thinking I could get control over you pretty fast if I tried.''



``Fuck,'' she said.  ``I think we'd both be happier if you didn't.''



``Oh?  You going to tell me the Nine will come after me if I don't let you go?''



She shook her head, then used one hand to brush the hair away from her face.  ``No.  This.''



She reached inside her jacket, and Alec made her hand seize up, the fingers striving to bend the opposite way.



``It's cool,'' she said.  She winced with pain, then used her splayed hand to work a metal case the length of her forearm out into plain view.  It dangled from a thick cord that stretched around her neck.  ``See this?''



``Yep.''



``It's a bomb.  Very simple.  A block of explosives rigged to a timer.  Any time I call the right number, the timer will reset.  I did make the mistake of letting my phone battery die, but I figure I've still got a couple of minutes.  If you keep me here for any longer than that, I go kablooie.''



``Is that a threat?  Sounds like a win for me.''



``You'll probably get blown up as well.  Or maimed,'' she smiled.



``I could walk away.''



``And lose control over your minions as you get further away?  Please do.  I can make the call when you're gone.''



His emotions were so muted.  Dim.  How much of that was Jean-Paul or Alec's personality, and how much was his natural immunity, built up over years of exposure to Daddy?  She couldn't get a sense of what he was feeling, which was disappointing.



However faint his feelings were, she could sense the slightest change.  A chime of attention.  He didn't look at any of the puppets that he was struggling to control, but she could sense his attention flicker to the woman.  A thrum of confidence.



They both dashed towards the woman at the same moment.  In their hurry to get to her, they collided, falling to the ground as a trio.



The woman wasn't in any shape to fight, but Alec did strike Cherie across the head, fairly ineffectually.  She retaliated by kicking him, then grabbed his wrist as he tried to draw the weapon he had in his pocket.  It was a gold-painted stick topped with a crown.  She couldn't see why he wanted it, but he did and so she wasn't about to let him have it for just that reason.



He changed tactics, rolling over to drive one shoulder into Cherie.  With his free hand he tried to reach for the gun holster worn by the woman.  \emph{That} had been what caught his attention, gave him that surge of confidence.  Cherie fought with him, pulling him away, and then got one leg under him to roll him away.  She pinned him, holding his wrists to the floor.



``Got you, little brother.  You still suck at fighting.''



He stared up at her, panting for breath and looking half-bored at the same time.  He used his power, and she let go of his left hand to strike him across the face.  He stopped.



She smiled, ``Thought you should know that things got pretty shitty at home after you left.  Daddy got really overprotective, angry.  It sucked.  Sucked worse when we couldn't find you.''



``Sorry,'' he said, in what she judged as the least convincing tone he could manage.



``My payback?  I've nominated you for the Nine.''



``Not interested.''



``Doesn't matter.  You get nominated, you're tested no matter what you want\ldots and a few of the Nine don't want to have two Vasils on the same team.  Shatterbird hates my guts, for some reason.  Crawler doesn't respect me.  Jack thinks it would be boring.  So what I'm thinking is that this test?  The initiation?  It's going to be a little harder for you.  They won't be testing you to see if you're mean enough, bloodthirsty enough, creative enough.  They're just going to try to kill you.''



``Fuck,'' Alec said, his eyes widening.



``Have fun with that,'' she smiled, standing.  She had to leap back to avoid being stabbed with the gold-painted stick as she released his wrist.  ``Now we're even.''



``Fuck you.  That's not even at all!  I leave home, so you arrange to have me killed by some of the scariest fuckers on this side of Earth?''



``Yep,'' she smiled, smug.  It was good to see she could provoke him, get a response out of him.  Was that because she'd done it well, or had he gotten more emotional as of late?



He ran his fingers through his hair.  ``Lunatic.''



``What I find \emph{really} interesting is that you've got some connections.  A girlfriend, maybe?  No.  Nothing romantic.  You have friends?  A team?''



He stayed silent.



``Come after me, I go after them.  You may be immune, but they aren't.''



``Fine.''



``And remember, I can always tell Daddy where you are.  He's pissed you left.  Pissed \emph{I }left, but he's too scared to come after me.  Not with the Nine having my back.''



``They don't have your back, Cherie.''



She shrugged.  ``Close enough.''



``No.  They're going to kill you someday.  Probably sooner than later, when you're no longer useful and they want the thrill of the hunt again.  You've probably seen what they can do.  Fates worse than death.  Just don't ask for \emph{my} help when you realize it's happening.''



``Whatever.''



``You just screwed me over, Cherie.  Don't know why you did it, but I think you did a pretty fucking good job of it.  You trying to be like Jack?  Trying to act like them, pretend you have a place there?  Rest assured, you screwed \emph{yourself }ten times as bad as you screwed me.''



She scoffed at that.



``You're way out of your depth.  As good as you think you are, they're \emph{better}.''



She smiled and shook her head, ``We'll see.  I'm gonna leave now.  You're going to let me.  Cool?''



He sighed.  ``Can't really stop you or you'll fuck with my team, right?''



``Right.  But first\ldots''  She bent down and searched the woman who was sweating, panting, and twitching with the combination of Cherie's emotional assault and Alec's physical control.  She found the gun, and then found a cell phone.  She dialed the number to reset the timer on the bomb she wore.



She felt a touch relieved as the call went through.  That could have been a pretty lethal mistake on her part.  She'd have to break her rule and buy a cell phone charger.



``Bye, baby brother.''



``Go die horribly, sis.''



She smirked and turned to leave, putting a touch of extra sway into her walk as she made her way out the door.



She \emph{had} this.  A few weeks, one or two months at the most, she could be one of the most dangerous people in the world, barring the obvious exceptions like the Endbringers.



What Alec didn't know was that her power \emph{did }have long-term effects.  Subtle, but they were there.  Emotions were like drugs.  People formed dependencies and tendencies.  If she hit someone with a minute amount of dopamine every time they saw her, it would condition them until she didn't even need to use her power to do it.



\emph{Just a little while longer}, she told herself, \emph{and I'll have the Nine wrapped around my little finger.}





