





Amy sat on her bed, staring at the piece of paper in her hands.  The header at the top was stylized, a silhouette of a superhero with a cape flowing, with a script reading `The Guild' extending to the right.



Mrs. Carol Dallon.  Brandish,



Let me open by stating my condolences for the loss of your brother-in-law, nephew, and your husband's injury.  I have heard New Wave is currently considering disbanding, and you have my best wishes, whatever route you end up taking.  We have too few heroes and heroines to lose them, and even fewer of the truly good heroes and heroines who set the standard for everyone else, parahuman and human alike.  If finances ever become a concern, know that all you need to do is ask, and we will find you employment among the Guild's uncostumed staff.



Knowing what you have been through as of late, it is with a heavy heart that I send you this message with further bad news.  Marquis, interred in the Baumann Parahuman Containment Center, confided to another inmate that he fears for his daughter's life.  I have checked the facts to the best of my ability, and the details I have been able to dig up match with his story.  I must warn you that Allfather may have arranged for Amy Dallon to be murdered at some future date, in revenge for his own daughter's death at Marquis' hands.



She had to stop reading there.  The paper had been on Carol's bedside table, and Amy had found it while collecting a change of clothes for Mark a week ago.  Carol had probably been reading it to him late the previous night, and maybe forgot to put it away due to a mixture of exhaustion and the distractions that came with waking up each morning to a disabled husband and a ten-year career in jeopardy.



Amy knew she shouldn't have read it, but the header had caught her attention.  With her family's fate uncertain, she had found herself reading, to see if they were joining the Guild, if something else had happened that could distract them from this.



Now that door was open, and she could never shut it again.  She didn't care so much about the possible hit on her.  No.  What shook her was that she now knew who her father was.  She even suspected that, like Tattletale had told her months ago, she'd always known.  She just hadn't dug for it, hadn't put the pieces together.



Marquis had been an aspiring crime lord in the bad old days of Brockton Bay.  It had been a time when the villains had been flocking to the city to profit off the booming tech and banking sectors, to recruit mooks and henchmen from the city's unemployed dockworkers.  It had been an era when the heroes hadn't been properly established, and the villains had been confident enough that some didn't give a second thought to murdering any heroes who got in their way.  Marquis included.



The bad old days were how Carol and Mark referred to that time.  There were more heroes now, and there was more balance between the good guys and the bad, but things were arguably worse now.  Everything was in shambles.



Marquis had been an osteokinetic.  A manipulator of both his own bone and, provided some was exposed, the bones of his enemies.  He'd been notorious enough that she'd heard about him despite the fact that he'd been arrested more than a decade ago, that the city and the public had remembered him.  He'd lived in the outskirts of the city, residing in a large house in the woods, just beneath the mountains.



She thought maybe there was something familiar about that idea.  Was it imagination when the vague image of a house popped into her mind?  The study with the black leather chair and countless bookshelves?  Or was it memory, something recalled from her early childhood?



To all reports, the man had been heartless, callous.  Wasn't \emph{she}?  She couldn't bring herself to care anymore when she went to the hospitals to heal the injured and sick.  It was a chore, something she made herself do because people wouldn't understand if she stopped.  There were only so many people she could heal before she became desensitized to it.



What else did she know about Marquis?  She vaguely recalled Uncle Neil talking about the man when he'd been talking to Laserdream about villain psychology.  There were the unpredictable ones, the villains who were hard to stop because you couldn't guess where they'd strike next, but who were less practiced in what they did and made mistakes you could leverage against them.  There were also the orderly ones.  The ones who were careful, who honed their methodology to perfection, but they repeated themselves, showed patterns that a smart hero could use to predict where they struck next, and often had rules or rituals a hero could turn against them.



Which wasn't to say that one was smarter than the other, or that one was better.  Each posed problems for the local authorities and capes.  Marquis had fit into the latter category, the perfectionists, the pattern killers.  He'd had, as Neil explained, a warped sense of honor, underneath it all.  He didn't kill women or kids.



Not hard to pull the pieces together.  She could remember how quickly Neil had dropped the subject when he realized she was listening.  He hadn't outright said that they'd caught Marquis, but she could imagine that the weaknesses that Neil had been outlining had been what they'd used.  Send Lady Photon, Brandish and Fleur against the man.  Add the fact that Amy had been there, a toddler, and Marquis had been too concerned about collateral damage to go all out.



It was him.  She didn't want it to, but it all fit together.



It was all so fucked up.  \emph{She} was so fucked up.



There was a knock on her door.  She hurried to hide the paper.



``Come in,'' she said, trying to compose herself in the span of one or two seconds.



Carol opened the door.  She was pulling on the gloves for her costume.  ``Amy?''



``Yeah?''



Carol took a few seconds before she looked up from her gloves and met Amy's eyes.  When she did, the look was hard, accusatory.



``There's word about some strange howling near the Trainyard.  Glory Girl and I are going on a patrol to check on it.''



Amy nodded.



``Can you look after Mark?''



``Of course,'' Amy said, her voice quiet.  She stood from her bed and headed to the door.  Carol didn't move right away.  Instead, Amy's adoptive mother stayed where she was, staring at Amy.  Amy reached the door and had to stop, waiting for Carol to speak.



But Carol didn't.  The woman turned and left the doorway, Amy meekly following.



\emph{They don't understand.}



Mark was in the living room, sitting on the couch.  No longer able to don his costume and be Flashbang, Mark could barely move.  He had a form of brain damage.  It was technically amnesia, but it wasn't the kind that afflicted someone in the movies and TV.  What Mark had lost were the skills he'd learned over the course of his life.  He'd lost the ability to walk, to speak full sentences, hold a pen and drive a car.  He'd lost more – almost everything that let him function.



What little he regained came slowly and disappeared quickly.  It was as though his brain was a shattered glass, and there was only so much he could hold in it before it spilled out once again.  So they'd patiently worked with him, helping him to hobble between the bedroom, living room and bathroom.  They'd worked with him until he could mostly feed himself, say what needed to be said, and they didn't push him to do more.



Victoria was in costume as Glory Girl, but she was unclipping a bib from around his neck, something to ensure he didn't stain his clothes while he ate.  Amy's adoptive father turned and smiled gently as he saw the other two members of his family.  It was all Amy could do to maintain eye contact, smile back.



``Ready, mom?'' Victoria asked.



``Almost ready,'' Carol said.  She bent down by Mark and kissed him, and he was smiling sadly as she pulled back.  He mumbled something private and sweet that his daughters weren't privy  to, and Carol offered him a whispered reply.  Carol stood, then nodded at Victoria, ``Let's go.''



They left without another word.  There was no goodbye for Amy, no hug or kiss.



\emph{Victoria can't even meet my eyes}.



The slight hurt more than she'd expected.  It wasn't like it was something new.  It had been going on for weeks.  And it was fully deserved.



Amy felt her pulse pounding as she looked at Mark.  Made herself sit on the couch next to him.  \emph{Does he blame me?}



It was all falling apart.  This family had never fully accepted her.  Being in the midst of a family that all worked together, it was hard to preserve secrets.  Amy had learned a few years ago, overhearing a conversation between Carol and Aunt Sarah, that Carol had initially refused to take her in.  Her adoptive mother had only accepted in the end because she'd had a job and Aunt Sarah didn't.  One kid to Aunt Sarah's two.  When she'd taken Amy in, it hadn't been out of love or caring, but grudging obligation and a sense of duty.



Mark had tried to be a dad.  He'd made her pancakes on the weekends, taken her places.  But it had always been inconsistent.  Some days he seemed to forget, others he got upset, or was just too distracted for the trips to the ice cream store or mall.  Another secret that the family hadn't kept – Mark was clinically depressed.  He had been prescribed drugs to help him, but he didn't always take them.



It had always been Victoria, only Victoria, who made her feel like she had a family here.  Victoria was mad at her now.  Except mad wasn't the right word.  Victoria was appalled, seething with anger, brimming with resentment, because Amy couldn't, \emph{wouldn't}, heal their father.



They'd fought, and Amy hadn't been able to defend her position, but still she'd refused.  Every second that Victoria and Carol spent taking care of Mark was a second Amy felt the distance between her and the family grow.  So she took care of Mark as much as she could, only taking breaks to visit the hospitals to tend to the sick there.  She'd also needed a few to process the letter she'd received.



The letter.  Carol wasn't angry in the same way Victoria was.  What Amy felt from her `mother' was a chill.  She knew that she was only justifying the darker suspicions Carol had harbored towards her since she was first brought into the family.  It was doubly crushing \emph{now}, because Amy knew about Marquis.  Amy knew that Carol was thinking the same thing she was.



Marquis was one of the organized killers.  He had his rules, he had his code, and so did Amy.  Amy wouldn't use her power to affect people's minds.  Like father, like daughter.



``Do you need anything?'' she asked Mark, when the next ad break came up.



``Water,'' he mumbled.



``Okay.''



She headed into the kitchen, grateful for the excuse to leave the room.  She searched the dishwasher for his cup, a plastic glass with a textured outside, light enough for him to lift without having to struggle with muscle control, easy enough to grip.  She filled it halfway so it wouldn't be as heavy.



Tears filled her eyes, and she bent over the sink to wash her face.



She was going to lose them.  Lose her family, no matter what happened.



Which meant she had to go.  She was old enough to fend for herself.  She would leave of her own volition, and she would help Mark as a parting gift to her family.  She just had to work up the courage.



Drying her face with her shirt, she carried the mug into the living room.



The TV was off.



Had Mark turned it off because he'd wanted to sleep?  Amy was careful to be quiet, stepping on the floorboards at the far sides of the hallway so they wouldn't creak.



A girl stood in the living room, five or so years younger than Amy.  Her blond hair had been curled into ringlets with painstaking care, but the rest of her was unkempt, filthy.  She stared at Mark, who was struggling and failing to stand from the couch.



The girl turned to look at Amy, and Amy saw that some of the dirt that covered the girl wasn't dirt, but crusted blood.  The girl wore a stained apron that was too large for her, and the scalpels and tools in the pocket gleamed, catching the light from the lamps in the corner of the room.



Amy recognized the girl from the pictures that were hung up in the office.



``Bonesaw.''



``Hi,'' Bonesaw gave a little wave of her hand.  A wide smile was spread across her face.



``What- What are you doing here?''



``I wanted to see you.  Obviously.''



Amy swallowed.  ``Obviously.''  Was it possible that Allfather had arranged for a member of the \emph{Slaughterhouse Nine} to murder her?



Amy's eyes roved over the room, looking for Bonesaw's work.  Nothing.  She looked over her shoulder and a shriek escaped through her lips.  A man was not two feet behind her, tall and brutish, his face badly scarred and battered to the point that it was barely recognizable as human.  A long-handled axe sat in one of his massive, calloused hands, the head resting on the floor.  \emph{Hatchet Face}.



``Runnn,'' Mark moaned, urging her.  She didn't give it a second thought.  She dashed for the front door, threw it open with enough force that a picture fell from the wall.



Hatchet Face stood on the other side, blocking the doorway.



``No,'' she gasped, as she backed towards the living room, ``No, please.''



How?  How had he gotten there so fast?  She turned around and saw he was still there, still in the hallway.



There were \emph{two} Hatchet Faces?



Then the first one exploded into a cloud of white dust and blood spatters, momentarily filling the room.  Amy could hear Bonesaw's giggling, felt her heart sink.



``Get it?  You figure out what I did?  Turn around, Hack Job.''



Amy had figured it out, but Bonesaw's creation demonstrated anyways.  He turned his back to Amy, and she saw what looked like a tumorous growth on the back of his head, shoulders and arms.  Except the growth had a face, vaguely Asian in features, and the lumps inside the growth each roughly corresponded with organs and skeletal structure.  The jaw of the figure that was attached to the back of Hatchet Face's body was working open and closed like a fish gasping for air.  The stitches were still fresh.



``You mashed them together.  Oni Lee and Hatchet Face.''



``Yes!  I can't even begin to tell you how hard it was.  I mean, I had to conduct the operation from a remote location, using robots, because I would lose my Tinker powers if I got too close to the big lug.  And I had to fit their bodies and nervous systems together so that they could use their powers without messing up the other.''



``Oh god,'' Amy mumbled.  \emph{Is this what she's going to do to me?}



``Had to add in a control frame and perform a spot lobotomy so Hatchet would obey me, you know.  He didn't lose much.  Was never very bright.''



``And Oni Lee?'' Amy was almost afraid to ask.



``Oh, I barely touched his brain.  He suffered some moderate brain damage from his close brush with death, but I revived him.  His brain's more or less intact, even.  He can't control his body, but he's alert and aware, and he feels everything Hatchet does,'' Bonesaw smiled wider.



``That's horrifying.''



``It's not a perfect mesh.  I only just started doing these mash-ups.  Still practicing.  Hatchet's power isn't working as well anymore, and I'm worried about physical wear and tear as they teleport, but it's still one of my better works.  Took me four whole hours.''  Bonesaw clasped her hands in front of her, shifting her weight from foot to foot, waiting expectantly.



Amy swallowed.  She didn't have words.



Bonesaw smiled.  ``I thought you'd appreciate this more than anyone.''



``Appreciate this.''



``You're the only other person who works with \emph{meat}.  I mean, we're different in some ways, but we're also really similar, aren't we?  You manipulate people's biology, and I \emph{tinker} with it.  The human body's only a really intricate, wet machine, isn't it?''



Others were entering the room now.  From the kitchen, a woman, the structure of her face altered into something that was more rat-like than human, conelike, ending in a squashed black nose that had staples around it.  Bonesaw had added a second set of teeth, all canines, so that the woman would have enough as her jaw was stretched forward.  Drool constantly leaked between her teeth in loops and tendrils.  She was pale, except for her face and patches all down her body, where patches of ebon black skin were stapled in place.  Her hair was long, dark, and unwashed, but most unnerving of all were her fingers, which had been replaced by what looked like machetes.  The clawtips dragged on the hardwood as she stumped forward on feet that had been modified in a similar way, no longer fit for conventional walking.



The third was another Frankenstein hodgepodge of two individuals, emerging from the hallway where the amalgamation of Oni Lee and Hatchet Face -Hack Job- had exploded.  The lower half was a man who must have been built like a gorilla in life, rippling with muscles, walking forward on his knuckles.  His upper body grew up from the point the other body's neck should have begun, an emaciated man with greasy brown hair and beard, grown long.  He was not unlike a centaur, but the lower half was a brutish man.



Then there were the other things.  They weren't alive.  Spidery contraptions of scrap metal, they lacked heads, only consisting of a box half the size of a toaster and spindly legs that moved on hydraulics, each ending in a syringe or scalpel.  A dozen of them, climbing onto the walls and floor.



``Murder Rat used to be a heroine, called herself the Mouse Protector.  One of those capes who plays up the cheese, no pun intended.  Camped it up, acted dorky, used bad puns, so her enemies would be \emph{embarrassed} to lose to her.  Ravager decided she'd had enough, asked the Nine to take Mouse Protector down.  So we took the job.  Beat Mouse Protector, and I took her to the operating table.  The other Nine tracked down Ravager and collected her, too.  Just to make it clear that we don't take orders.  We aren't errand boys or errand girls either.  Now Ravager gets to spend the rest of her life with the woman she hated, making up.''



Amy swallowed, looking at the woman.



``The other, I'm trying to figure out a name.  The one on the bottom was Carnal.  Healer, tough, and healed more by bathing himself in blood.  Thought he had a place on our team, failed the tests.  The one on the top was Prophet.  Convinced he was Jesus reborn.  What do you call a mix of people like that?  I've got a name in mind, but I can't quite figure it out.''



``I don't know.''



``So you're bad at names too?'' Bonesaw grinned.  ``I'm thinking something like shrine, temple\ldots but one with multiple floors.  Um.''



``Pagoda?''



``Pagoda!  Yes!''  Bonesaw skipped over to her creation, wrapped her arms around one of his, ``Pagoda!  That's your name, now!''



None of the three monsters moved or reacted.  Each stared dumbly forward, Murder Rat drooling, the others appearing to be in a daze.



``That's good!''  Bonesaw smiled at Amy, ``I knew we'd make a good team!''



``Team?''  What could she say or do to escape?  Failing that, was there anything she could use to kill herself, so Bonesaw couldn't get her hands on them, turn them into something like those things?  In the worst case scenario, she could use her power on Mark before finishing herself off.



Except she wasn't sure it would matter.  Amy was incapable, but there was nothing saying Bonesaw couldn't raise the recently dead.



``Yes, team!  I want you to be my teammate!''  Bonesaw was almost gushing.



``I don't-'' Amy stopped herself, ``Why?''



``Because I always wanted a big sister,'' Bonesaw replied, as if that was answer enough.



Amy blinked.  Sister.  She thought of Victoria.  ``I make a pretty shitty sister.''



``Language!''  Bonesaw admonished, with surprising fierceness.



``I'm sorry.  I- I'm not a very good sister, I don't think.''



``You could learn.''



``I've tried, but\ldots I've only gotten worse at it as time passed.''



Bonesaw pouted a little.  ``But think of the stuff we could do together.  I do the kludge, the big stuff, you smooth it over.  Imagine how Murder Rat would look without the scars and staples.''



Amy looked at the onetime heroine, tried to picture it.  It wasn't any better.  Worse, if anything.



``That's only the beginning.  Can you even imagine the things we could make?  There's no upper limit.''



There was a beep from the answering machine.  It began playing a message.  ``Amy, pick up!  We're looking at dealing with Hellhound, and there's injured.  Call Aunt Sarah or Uncle Neil over to look after dad and get over to the-''



The message cut off, and there was the sound of a clatter, a distant barking sound.



``I don't think I have it in me to do stuff like that,'' Amy said.  \emph{If nothing else, I can't disappoint Victoria any further}.



``Oh.  Oh!''  Bonesaw smiled.  ``That's okay.  We can work through that.''



``I- I don't think we really can.''



``No, really,'' Bonesaw said.  Then she snapped her fingers.



Hack Job flickered into existence just in front of Amy, and there was little she could do to escape.  She cried out as the man's massive hand smashed her down onto her back, a few feet from Mark.



Mark struggled to stand, but Murder Rat darted across the room to light atop the back of the couch and press one of her three-foot long claws against his throat.



Amy was pinned.  She tried to use her power on Hack Job through the contact he was making with her chest and neck, only to find it wasn't available.  She couldn't sense his body, the blood flowing in his veins, or any of that.  Even her own skin felt quiet, where she normally felt the pinprick sensations of innumerable, microscopic airborne lifeforms touching her.  She'd barely even realized that was happening until it stopped.



``Jack's taken me on as his proteg\'{e}.  Teaching me the finer points of being an \emph{artist}.  What he's been saying is that I'm too focused on the external.  Skin, bone, flesh, bodies, the stuff we see and hear.  He's told me to practice with the internal, and this seems like a great time to do that.''



``Internal?'' Amy replied.



``It's \emph{easy} to break people's bodies.  Easy to scar them and hurt them that way.  But the true art is what you do inside their \emph{heads}.  Do you have a breaking point, Amy?  Maybe if we find your limits and push past them, you'll find yourself in a place where you'll want to join us.''  A wide smile spread across Bonesaw's face as she settled into a cross-legged position on the floor, facing Amy.



``I- no.  Please.''



``You're a healer, but you can do so much more.  Why don't you go out in costume?''



Amy didn't respond.  There was no right answer here.



``Are you afraid to hurt someone?  That could be our first exercise.''



Amy shook her head.



``Murder rat, come here.  Hack Job, back off.''



Hack Job let go of her, and she tried to scramble away, but Murder Rat pounced on her, pressing her down against the ground.  The woman smelled rank, like a homeless person.



``So here's the lesson,'' Bonesaw said, ``Hurt her, take her apart.  If you go easy on her, or if you leave her in a state where she can move, she'll cut you, and then she'll cut a body part off that man on the couch there.''



Murder Rat placed a blade against her cheek, scraped it down toward her chin, as if giving Amy a close shave.



She reached up and touched the woman's chest.  Without Hack Job touching her, her power was coming back quickly.  She felt Murder Rat's biology snap into her consciousness, until she could see every cell, every fluid, every part of the woman.  The two women.  She could see Bonesaw's work, the integration of body parts, the transfusions of bone marrow from one woman to the other, the viruses with modified DNA inside them, skewing the balances and configurations until she couldn't tell for sure where one woman started and the other began.



She could also see the metal frames inside the woman, interlacing with the largest bones of her skeletal system, the needles in her spine and brain.  Bonesaw's control system.  There was something around the heart, too.  Metal, with lots of needles pointing inward.  She was rigged to die if the control frame was ever disabled.  The woman, no, the \emph{women}, were awake in there.  One and a half brains contained in a synthetic fluid in her skull.



She targeted the ligaments at the woman's shoulders and hips.  Cutting them was easier than putting the things back together again.  Dissolve the cells, break them down.



The woman collapsed onto a heap on top of her.



``Excellent!  Pick her up, H.J.''



Hack Job picked up the limp Murder Rat, put her down a short distance away from Amy.  Bonesaw walked over to her creation and propped up Murder Rat so she had a view of the scene.



``I'm surprised you didn't kill her.  The healer, letting someone suffer like that.  Or are you against mercy killing?''



Again, there was no answer she could give that wouldn't worsen her situation.



``Or are you against killing in general?  We can work on that.''



``Please.  No.''



``Pagoda.  Your turn.''



Pagoda approached with an awkward lurch, and Amy managed to stand and run.  She got halfway to the front door before Hack Job materialized in front of her, barring her way.  He pushed her, and she fell.  Pagoda lurched over to her and pressed her down.



``I use my creations to collect material for other work.  It's a circle, using them to get material for more creations.  Having the Nine was essential to get things started, and to help get things going again if a hero managed to put down a few, but now I'm in good shape.  I stick around because they're mostly fans, and they're kind of family.  I want you in my family, Amy Dallon.''



``Please.''



``Now, I'm willing to make sacrifices to see that happen.  Same thing as with Murder Rat.  You don't stop Pagoda, I'll have him hurt the man on the couch.''



Amy used her power on Pagoda, felt his body, much the same as Murder Rat's in so many respects, though the metal frame with the needles in his spine was different.  She reached for the ligaments at his shoulders and hips, separated them.



The first had grown back before she'd started on the third.



``He heals,'' Bonesaw informed her.  ``Two regenerators in one.  There's only one good way to stop him.  Try again.''



Pain.  She inflicted pain on Pagoda.  No reaction.  She'd have to reach into his brain to make it so he really felt pain again.  She tried atrophying his muscles, with no luck.  Anything she did was undone nearly as fast as she could inflict it.



``Five seconds,'' Bonesaw announced.  ``Four.''



Sending signals to his arms to get him to move.  No.  The metal frame overrode anything she could do with her power to control him.



``Three.''



Amy used the only option available to her.  She disconnected him from the metal frame that Bonesaw used to control her subjects.  She could sense it as the metal shifted into motion around his heart.  Not needles, as there had been for Murder Rat, but small canisters of fluid.



``Two\ldots one\ldots zero point five\ldots Ah, there we go.''



Pagoda lurched backward and broke contact with Amy, her power no longer giving her an insight into what was happening with him.  He sat down, using one hand to prop himself up.  A moment later he slumped over, his eyes shutting.  His breathing stopped.



``A chemical trigger for something I already put in his DNA, when I was patching his regeneration abilities together.  Reverses the regeneration so it does the opposite, starting with the heart.''



Amy looked at her hand.  She'd just taken a life.  A mercy, most probably, but she'd killed.  Something she had promised herself she would never do.



She shivered.  It had been so easy.  Was this what it was like for her father?  Had she just taken one more step toward being like him?



``Ready to join?'' Bonesaw asked, looking for all the world like a puppy when her master had the leash out, ready for a walk.  Eager, brimming with excitement.



``No,'' Amy said.  ``There's no way.''



``Why?  Whatever's holding you back, we can fix it.  Or we can break it, depending.''



``It's not- don't you understand?  I don't want to hurt people.''



``But we can change that!  We're not so different.  You know as well as I do that anything about anyone can be changed if you work hard enough.''



``Then why don't you change?  You could be good.''



``I like the other members of the Nine.  And I couldn't make anything really amazing if I was following rules.  I want to make something even more amazing than Hack Job, Murder Rat or Pagoda.  Something you and I could only make together.  Can you imagine it?  You could use your power, and then we could make one superperson out of a hundred capes, and all of the powers would be full strength because you helped and we could use it to stop one of the Endbringers, and the whole world would be like, `Are we supposed to clap'?  Can you picture it?''  Bonesaw was getting so excited with her idea that she was almost breathless.



``No,'' Amy said.  Then, just to make it clear, she added, ``No, it's not going to happen.  I won't join you.''



``You will!  You have to!''



``No.''



``I have to do like Jack said.  He said I won't be a true genius until I've figured out how to get inside people's heads.''



``Maybe- Maybe you won't be inside my head until you realize there's no way I'm going to join the Slaughterhouse Nine.''



Bonesaw frowned.  ``Maybe.''



Amy nodded.



``Or maybe I need to figure out your breaking point.  Your weak spot.  Like that man there.''  Bonesaw pointed at Mark. ``Cherish said you sleep here, and you've been around him for a while\ldots so why haven't you healed him?''



Amy shivered.



``Who is he?''



``My dad.''



``Why not fix your dad?''



``My power doesn't work on brains,'' Amy lied.



``You're wrong,'' Bonesaw said, stepping closer.



``No.''



``Yes.  Your power \emph{can} affect people's brains.  You have to understand, I've taken twenty or thirty people apart to figure out how their power works so I can put them back together again the way I want them.  I've learned almost everything about powers.  I've induced stress of all kinds on people until they had a trigger event, while I had them on my table and wired to computers, so I could record all the details and study their brains and bodies as the powers took hold.''



Twenty or thirty people she's taken apart.  However many others she's tortured to death.



Bonesaw smiled, ``And I know the secrets.  I know where powers come from.  I know how they work.  I know how \emph{your} power works.  You have to understand, people like you and me?  Who got our powers in moments of critical stress?  The powers aren't meant for us.  They're accidents.  \emph{We're} accidents.  And I think you could see it if you were touching someone when they had their trigger event.''



``I don't understand.''



``You don't have to.  What you need to know is that the subjects of our power, the stuff it can work on, like people?  Like the fish lady in Asia?  The boy who can talk to computers?  Our powers weren't created to work with those things.  With people or fish or computers.  It's not intentional.  It happens because the powers connect to us in the moments we have our trigger events, decrypt our brains and search for something in the world that they can connect to, that loosely correlate with how the powers were \emph{originally} supposed to work.  In those one to eight seconds it takes our powers to work, our power goes into overdrive, it picks up all the necessary details about those things, like people or fish or computers, sometimes reaching across the whole world to do it.  Then it starts condensing down until there's a powerset, stripping away everything it doesn't need to make that power work.''



Amy stared.



``And then, before it can destroy us, before we can hurt ourselves with our own power, before that spark of potential burns out, it changes gears.  It figures out how to function with us.  It protects us from all the ways our power might hurt us, that we can anticipate, because there's no point if it kills us.  It connects with our emotional state at the time the powers came together, because that's the context it builds everything else in.  It's so amazingly complicated and beautiful.''



Bonesaw looked down at Amy.  ``Your inability to affect brains?  It's one of those protections.  A mental block.  I can help you break it.''



``I don't want to break it,'' Amy said, her voice hushed.



``Ahhh.  Well, that just makes me more excited to see how you react when you do.  See, all we have to do is get you to that point of peak stress.  Your power will be stronger, and you'll be able to push past that mental block.  Probably.''



``Please,'' Amy said.  ``Don't.''



Bonesaw reached into her apron and retrieved a remote control.  She pointed it at Mark, where he sat on the couch.  A red dot appeared on his forehead.



``No!''



One of Bonesaw's mechanical contraptions leaped across the room, its scalpel legs impaling the suede cushions on either side of Mark.  One leg, tipped with a syringe, thrust into Mark's right nostril.  He hollered incoherently, tried to pull away, only for two mechanical legs to clutch his head and hold him firm.



Amy's screams joined his.



``I'm doing you a favor, really!''  Bonesaw raised her voice to be heard over the screams.  ``You'll thank me!''



Amy rushed forward, hauled on the metal leg to pull it from Mark's nostril, pulled at the other legs to tear it from him and then hurled it away.  Lighter than it looked.



``Now fix him or he'll probably die or be a vegetable,'' Bonesaw told her.  ``Unless you decide you're okay with that, in which case we're making progress.''



Amy tried to shut out Bonesaw's voice, straddled Mark's lap and touched his face.



She'd healed him frequently in the previous weeks, enough to know that he was remarkably alert in a body that refused to cooperate or carry out the tasks he wanted it to.  Not so different from Bonesaw's creations in that respect.  She'd healed everything but his brain, had altered his digestive system and linked it to his circadian rhythms so he went to the bathroom on a strict schedule, to reduce the need for diapers.  Other tune-ups she'd given him had been aimed at making him more comfortable, reducing stiffness and aches and pains.  It was the least she could do.



Now she had to focus on his brain.  The needle had drawn ragged cuts through the arachnid layer, had injected droplets of acid into the frontal lobes.  More damage, in addition to what Leviathan had inflicted with the head wound, and it was swiftly spreading.



Everything else in the world seemed to drop away.  She pressed her forehead to his.  Everything biological was shaped in some way by what it had grown from and what had come before.  Rebuilding the damaged parts was a matter of tracing everything backwards.  Some of the brain was impossible to restore to what it had once been, in the most damaged areas or places where it was the newest growths that were gone, but she could check everything in the surrounding area, use process of elimination and context to figure out what the damaged areas had tied to.



She felt tears in her eyes.  She had told herself she would heal him and then leave the Dallon household.  Actually doing this, fixing him, taking that plunge, she knew she would probably never have found the courage if she hadn't been pushed into it.



It wasn't that she was afraid to get something wrong.  No.  Even as complicated as the mind was, she'd always known she could manage it.  No, it was what came after that scared her more than anything.  Just like finding out about Marquis, it was the opening of a door she desperately wanted to keep shut.



She restored his motor skills, penmanship, driving a car, even the little things, the little sequences of movements he used to turn the lock on the bathroom door as he closed it or turn a pencil around in one hand to use the eraser on the end.  Everything he'd lost, she returned to him.



He moved fractionally.  She opened her eyes, and saw him staring into her eyes.  Something about the gaze told her he was better.



``I'm sorry,'' she murmured.  ``I'm so sorry.''  She wasn't sure what she was apologizing for.  For taking so long to do it, maybe.  Or for the fact that she would now have to leave.



His attention was on his hands.  She could feel it through her contact with him, the power he was just barely holding back.  And Bonesaw?  The little lunatic was somewhere behind her.



She drew Mark's hands into his lap, between her body and his, where Bonesaw would be less likely to see.



An orb of light grew in his hands.



``It worked!  Yes!'' Bonesaw crowed.



Mark flicked his eyes in one direction, offered the slightest of nods, his forehead rubbing against hers.  Amy flung herself to one side as Mark stood in one quick motion, flinging the glowing orb at the little girl.



Hack Job flickered into existence just in time to have to orb bounce off his chest.  It exploded violently, tearing a hole into his stomach and groin.  The villain flew backward, colliding with Bonesaw.



But two more copies of Hack Job had already appeared, and the scalpel spiders were responding to some unknown directions, leaping for Mark and Amy.



Amy grappled with one spider, struggled to bend its legs the wrong way, cried out as the scalpels and needlepoints of the other legs dragged against her skin.



A blast sent her tumbling, throwing her into the couch and dislodging the spider.  Mark could make his orbs concussive or explosive.  He'd hit the spider with the former, nothing that could seriously hurt Amy.  She climbed to her feet, picked up the oak side-table from beside the couch and bludgeoned the spider with it.



More explosions ripped through their living room as Mark continued to open fire, hurling the orbs with a ferocity that surprised Amy.  When Hack Job tried to block the shots with his bodies, Mark bounced them between Hack Job's legs, off walls and off the ceiling.  Almost as if he could predict what his enemy would do, he lobbed one orb onto the couch.  It exploded a half-second after one of Hack Job's duplicates appeared there.



More duplicates charged from either direction, and Mark dropped a concussive orb at his feet, blasting himself and one of the duplicates in opposite directions.  He quickly got his footing and resumed the attack, fending off one duplicate that turned his attention to Amy, then going after Bonesaw.



Bonesaw had retreated into the hallway that led into the bedrooms at the back of the house, the basement and the kitchen at the side.  Mark threw an orb after her, obliterating the hallway, but Amy couldn't see if he'd struck home, not with the clouds of dust that were exploding from Hack Job's expired duplicates.  Between the time it had taken to create the orb, throwing it and the lack of a scream after it had gone off, Amy knew Bonesaw would have gotten away.



There was an extended silence.  Bonesaw and Hack Job were gone, leaving only Pagoda's body and the limp Murder Rat.  Long seconds passed as the dust settled.



``That woman.  Can you help her?''  Mark's voice sounded rough-edged.  It hadn't been used in its full capacity for a long few weeks.



``Her mind is gone, and not in a way I think I could fix,'' her voice was hushed.



``Okay.''  Mark walked over to Murder Rat and adjusted her position against the wall until she was more horizontal, almost lying down.  He crossed her claws over her chest, and then formed an orb of light the size of a tennis ball.



``Rest in peace, Mouse Protector,'' he said.  He placed the orb of light in the gap where two claws crossed one another, just over her heart, then stepped away.



There was a small explosion and a spray of blood.



``I'm sorry,'' Amy said, ``So sorry I didn't help you sooner, that-''



Mark stopped her with a raised hand.  ``\emph{Thank you}.''



She didn't deserve thanks.



``Are you okay?'' He asked.



She looked away.  Tears were welling out.  ``No.''



``Listen.  Sit yourself down.  I'm going to call your mother and sister, make sure they're all right after dealing with Hellhound, let them know what happened.  Then I'll call the Protectorate.  Maybe they can help guard us, in case Bonesaw comes after you again.''



``She will.  But I- I can't sit.  I'm going to my room.  I'll pack so we leave sooner.''



``You sure?''



She nodded.



``Shout if \emph{anything} happens.''



She nodded and turned to go, picking her way through the destroyed hallway.  The floorboards that looked like a giant-sized version of pick-up-sticks.  She was only halfway when she heard Mark on the phone.



``Carol?  It's me.''



Her face burned with shame.  She made her way to her room and began packing her things into a gym bag.  Clothes, toiletries, and other things, mementos.  A small scrapbook, a memory card filled with pictures of her, her cousins and her sister.  She found a pad of post-it notes and scribbled out a few words.



I'm sorry it took me so long to help Mark.



Good bye.  I love you all,



Amy.



She wouldn't be coming back.



Amy opened her bedroom window and climbed out, pulling the bag out behind her.



It would be better this way.  Maybe, after weeks or months, she could stop worrying, stop waiting for the other shoe to drop, for everything to fall apart in the worst way.  She'd already had to face finding out about Marquis.  She'd taken a life.  She'd broken one of her cardinal rules.  She wasn't sure she could take any more.



She just had to get away.



\blacksquare



Amy cursed the curfew as she saw the figure in the air above her.  When people weren't allowed out on the streets after dark, it made those few who \emph{did} venture out that much more visible.  Not what she'd wanted, not when she was trying to avoid this exact conversation.



It was even more problematic when she walked at maybe three or four miles an hour, limited to following the paths the roads and alleys allowed her, when her sister could fly at fifty miles an hour.  She should have hid, instead of trying to make some distance.



Victoria stopped midflight and hovered in the air, five feet above the ground and five or six paces in front of her.



``I was just at the house.  I don't even know what to say,'' Victoria spoke.



``Pretty self-explanatory.  One of the Nine came, house got trashed, I healed Mark.''



``Why?  Why heal dad now, when you couldn't before?''



``I only did it because I had to.''



``That's what I don't get.  Why couldn't you?  You've never explained.''



``I \emph{can't} tell you.''



``So that's it?  No explanations?  You just up and leave?'' Victoria asked.



``Yeah.''



``Why?''



Amy looked away.



``We could get you a therapist.  I mean, Mom was setting aside money for Dad's care, we could use that to give you someone to talk to.''



``I\ldots a therapist wouldn't be able to help.''



``Geez, what's going on?  Amy, we've been together for a decade.  I've stood by you.  I'd like to think we were best friends, not just sisters.  And you can't tell me?''



``I can't.  Just let me leave.  Trust me when I say it's better.''



``Fuck that!  I'm not about to let you walk away!''  Victoria floated closer, reaching out.



``\emph{Don't} touch me,'' Amy warned her sister.



Looking lost, Victoria stopped and spread her arms.  ``Who \emph{are} you, Amy?  I don't even recognize this person I'm looking at.  You go berserk at the bank robbery over some secret I've totally not gotten on your case about.  You apparently say something to Skitter that causes this huge commotion in the hospital after the Endbringer attack.  You\ldots I don't even know what to say about your reaction to Gallant's death, the way you distanced yourself from me at a time when I was hurting the most.''



Amy looked down at her feet.



``And most of all, you just leave dad to suffer, when you could have \emph{healed} him?  You lash out at me, here, when I'm trying to mend fences and be your sister?''



``You want to know who I am?'' Amy asked.  Her voice sounded hollow.  ``I'm \emph{Marquis's daughter}.  Daughter of a supervillain.''



``Marquis?''



Amy nodded.



``How did you find out?''



``Carol left some paper out.  I think it's under my pillow, if you want to look for it.''



``You have his genes, but you're Carol and Mark's daughter,'' Victoria replied, her voice firm.  ``And they're going to be worried.  Come home.''



``They don't \emph{care}.  They don't love me, not really.  Trust me, this is better for everyone.''



``\emph{I} love you,'' Victoria said, stressing the `I'.  She dropped to the ground and stepped closer.



``Don't touch me!''



``Idiot,'' Victoria grabbed her sister by the shirt collar and pulled her into a painfully tight hug.



``Don't,'' Amy moaned into her sister's shoulder.



``All of this?  We'll work it out.  \emph{As a family}.  And if your idea of family means it's just you and me, then we'll work it out together, just the two of us.''



All it took was one moment of weakness, and she \emph{was} weak.  At the end of her rope, desperately lonely, haunted by her father's shadow, her shame at being unwilling and unable to help Mark until now, the idea that one of the Slaughterhouse Nine thought she belonged with \emph{them}?



She was losing everything so quickly.  Victoria was all she had, and it was the choice between abandoning that for everyone's good and keeping Victoria close.



She felt Victoria's body more acutely than she felt her own.  Every heartbeat, every cell brimming with life.



Like a flame at the end of a long fuse, leading to a stick of dynamite, her power traveled from the side of Victoria's neck to her brain.  It was barely a conscious action on Amy's part.



Victoria let go of her, pushed her away.  ``What did you just do?''



Amy could see the revulsion slowly spreading across Victoria's face.



The magnitude of what she'd just done hit her with a suddenness and pain she likened to a bullet to the chest.  ``Oh god.  Please, let me undo it.''



She reached out, but Victoria stepped back.



``What the hell did you do?'' Victoria asked, her eyes wide, ``I felt \emph{something}.  I \emph{feel} something.  You've used your power on me before, but not like this.  I- You changed the way I think.  \emph{More} than that.''



Tears welled at the corners of Amy's eyes.  ``Please.  This is what I was afraid of.  Let me undo it.  Let me fix it and leave, and you can go back to Mark and Carol and you three can be a family, and-''



``What did you do!?''



``I'm sorry.  I\ldots \emph{knew} this would happen.  I was okay so long as I kept following my own rules, didn't open that door.  Bonesaw forced me to open it.''



``Amy!''



``You have to understand, for so long, you were all I had.  I was so desperately lonely, and that was at the same time I was starting to worry about my dad.  I got fucked up, my feelings got muddled somewhere along the line, and it's like\ldots maybe because you were safe, because you were always there.''



``You have feelings for me,'' Victoria answered.  She couldn't keep the disgust out of her voice, she didn't even try.  ``\emph{That's} what Tattletale was using as leverage, wasn't it?''



Amy couldn't meet Victoria's eyes.  She looked at her hands, appalled at what she had just done.



``And Gallant?  I was thinking you secretly liked him, but-''



Amy shook her head.  ``I \emph{hated} him.  I felt jealous because he had you and I never could\ldots but I \emph{never} acted on those feelings.  I never acted on \emph{any} of my feelings, until just now, and all I want to do is to take that back.''



``When I was at the lowest point in my life, when the boy I thought I might marry someday was dead, were you secretly elated?  Were you \emph{happy} Gallant died?''



``No!  Vic- Victoria, I \emph{love} you.  I wanted you to be happy with him.  I just\ldots it hurt at the same time.''



``Oh my god,'' Victoria whispered, the revulsion giving way to something worse.  Realization.



``I- I tried to keep things normal between us.  To act like your sister, keep it all bottled in.  It's just tonight was such a nightmare, and I'm so scared, and so tired, and so desperate.  Bonesaw forced me to ignore all the rules I was imposing on myself.  All the rules I was using and following so I wouldn't do anything stupid or impulsive.''



``Anything stupid.  Like what?  What did you do?''



Amy's voice was a croak as she replied, ``\ldotsmake it so you would reciprocate my feelings.''



She chanced a look at Victoria's face, and she knew that the horror she saw in her sister's expression didn't even compare to what she felt.



``Please.  Let me fix it.  Then I'll leave.  You'll never have to see me again.''



``What in the world makes you think I'd let you use your power on me again!?''  Victoria shouted, taking to the air, out of reach.  ``Who knows what you're going to do to me!?''



``Please?'' Amy begged.



``I can find someone else to fix it.  Or maybe, at the very least, I can show some \emph{fucking} self-control and realize it's my \emph{sister} I'm having those feelings about.''



``You can't.  I- Oh fuck.  You're underestimating what I did.  Please.  If you never ever give me anything else, if you never talk to me or look at me again, just let me fix this.''



Victoria shook her head slowly, then scoffed.  ``Good job, Amy.  You just did an \emph{excellent} job of taking every instance of me defending you, every instance of my giving you the benefit of a doubt, and proving me fucking wrong.  You were worried about being as fucked up as your dad?  Congratulations, I'm pretty \emph{goddamn} sure you just \emph{surpassed} the man.''



With that said, Victoria was gone, flying into the distance.



Amy sank to her knees on the flooded street.





