





I remained where I was, hands folded on the back of my head, kneeling, while the PRT officers bellowed at me, almost incoherent, impossible to obey as they gave me contradictory orders.  Down on the ground, stand up, throw any weapons to the side, do \emph{not} touch anything.



They were afraid to approach, too, apparently.  Maybe word had gotten out about what happened to Armsmaster when he'd gotten ahold of me at the fundraiser.  They each stopped about ten feet from me, forming a loose ring.  I'd thought they might have hit me with one of their nonlethal weapons, but they didn't shoot.  Maybe the audience was giving them second thoughts.



Miss Militia broke the stalemate, such as it was.  I could see her put one hand on Clockblocker's shoulder, giving him a gentle push.



In his white costume, he advanced.  He was inscribed with images of clocks in gray, some animated, little hands spinning at different speeds at his shoulder, the center of his chest, and the backs of his hands, places where the armor panels were broadest.  He crossed the perimeter of guards, getting closer to me.



When I didn't react, they seemed to take that as permission to move closer.  The bellowing reached a crescendo, and one officer was apparently unhappy that I wasn't already lying prone on the ground.  He planted a heavy boot between my shoulder blades, then thrust me into the ground.  I only barely managed to turn my head to avoid cracking my chin on the floor, pulling my head back so I didn't smash it.  I felt the air huff out of my chest, pain jolting through me.  My chest wasn't large, was a ways from `medium', even, but that didn't make it any better when it bore the brunt of the impact.



The other guards were alternately herding the civilians out of the area or forming a wall to keep them from watching.



``Hey!'' Clockblocker said.  ``That's enough.  I got this.''



The shouting stopped.  There was only the noise of the guards on the far ends of the room, giving orders to tourists and staff members, taking charge of the situation and escorting people out.



I had to twist my head to look up at Clockblocker.   For his part, he stared down at me, his expression hidden by the featureless white pane of his mask.



``This is a trick,'' he said.



``Yeah,'' I admitted.  ``But not the way you're thinking.''



He didn't respond to that.



``Do you need me to take a different position?'' I asked.



``Once upon a time, I would have had something clever to say in response to that,'' he said, quiet.



``What?''



``Nevermind.  Kneel, with your arms behind you.''



I moved slowly, so I wouldn't provoke any rash actions from the uniforms, climbing to my knees, then extending my arms behind me.



He reached out and touched the top of my head.



What felt like an instant later, my arms were weighed down.  Clockblocker was behind me, his hand on the heavy metal restraints to keep them from slamming into my tailbone.  Everyone else in the lobby had moved.  The Wards filled the area, along with the members of the Protectorate, new and old.  Flechette was only a short distance away, while Miss Militia stood just beside Clockblocker.  Even heroes that had presumably been on patrol were back, along with more PRT members than I'd counted in the building when I'd surrendered.



Tagg was there too, flanked by two PRT uniforms and one man who was wearing a suit, rather than a uniform.  The deputy director?



I'd lost control of my bugs while I'd been timed out.  In many cases, it wasn't a problem.  Still, I'd lost the ability to track most of those who were present, as mosquitoes, flies and ants went about their merry way.



``Stand,'' Miss Militia told me.



I tried to stand, but found more restraints on my ankles.  They were connected to the massive metal handcuffs I wore, which only made an awkward setup worse.



``Clockblocker,'' Miss Militia said.  She reached under one of my arms.  Clockblocker took her cue and did the same.  Together, they hauled me to my feet.  They stayed beside me, holding my arms, as they led me past all of the gathered heroes and PRT officers.  All people I'd hurt, people I'd \emph{humiliated}.



I had no friends here.



Director Tagg was lighting up a cigarette, despite the prominent `no smoking' signs nearby.  As I passed, he gave me a hard stare, heavily lined eyes glaring beneath thick black eyebrows, his face otherwise expressionless.  He pointed, and a PRT uniform joined our group.



Miss Militia handed me off to Triumph, and he helped Clockblocker lead me through the corridor to the PRT elevator.  The doors whisked shut, sealing the four of us inside.



\emph{Damn, }these handcuffs were uncomfortable.  They had to be a design meant for the heavy hitters, for capes who could rend steel with their bare hands.  Was it spite that made them use these cuffs?



They weren't reading me my rights.  Was there a reason?  I might have asked, but I didn't want to show ignorance.  Better to be confident, to act as if I knew exactly what was going on.



Above us, Tagg extinguished his cigarette, barely touched, fished in a nearby trashcan for a soda can, and dropped the butt inside before disposing of it.



I couldn't quite make out his words.  Not enough bugs in position.  ``-- \emph{now}.  PRT--''



All of the capes mobilized, joining Tagg and his immediate underlings in entering the stairwell.  The PRT moved as well, but in a wholly different direction.  They were taking defensive positions, leaders barking out orders.



I couldn't be absolutely sure, given how little I knew about guns, but I was pretty sure the PRT was packing more in the way of lethal weapons than they had been on my last visit.



The elevator stopped, so gently I might have missed it if my bugs didn't give me perspective on a larger scale.  We stepped out into a brightly lit hallway.



``This is an E-type containment cell.  Countermeasures include containment foam and these beauties,'' Triumph said.



\emph{Beauties?}



He was pointing up.  I followed the direction and looked.  Spheres the size of beach balls, chrome, with small windows on the bottom.  Familiar.



``Touch the door, make too much noise or use your power, and the room gets flooded with an electric charge,'' Triumph explained.  ``Calculated so it's only a \emph{little} less powerful than it'd need to be to do permanent damage.  Push it any further and the room is flooded with containment foam.  The same measures are packed into this whole hallway.''



\emph{Ah.  }They were the same devices that had been loaded into the drones that one of Dragon's suits had deployed.



``It's okay,'' I said.  ``I don't plan on escaping.''



``What \emph{are} you planning?'' Clockblocker asked.



``Don't engage her,'' Triumph said.  He brought us to a stop by one metal door.  There was a letter etched on the surface of the metal, a large `E', and smaller codes in boxes beside it.  M-21, CC-2, Bat-4



He tapped his phone against the wall, and two sets of metal doors slid open.  \emph{Very similar to the elevator}.  \emph{Same design}?



\emph{Thick walls}, I noted.  The walls that framed the door were a foot and a half deep.  It somehow made the small cell a little more claustrophobic.  It was daunting as it was, six feet by six feet, with sheet metal laid out over the floor and walls, welded together where they joined, with openings cut in where necessary.  There was a vent above me, pumping in a constant flow of fresh air, a little too cold, and another vent beneath the bed, blocked off by a grid of metal bars that extended between the bed and the floor.



The bed itself featured a mattress no thicker than my hand, covered in plastic and laid out on an arrangement of metal strips that wove into one another.  The `toilet' wasn't a toilet at all, but looked to be a urinal, horizontal and sunken into the ground, a shallow chrome basin with a drain and three thick buttons where it met the wall.  On the opposite wall, a television was set into the wall, protected by a clear pane.  I didn't see controls or anything resembling a remote.



Above me, another one of those beachball-sized orbs was embedded into the ceiling.  Ominous.



Everything was sealed and reinforced twice over.  Everything but the vents, but they were too small to crawl through.  \emph{Was this the kind of cell they put Lung in}?  With all the metal and the relatively meager amounts of cloth, I didn't imagine even his pyrokinesis would do much, unless he'd grown considerably.



I turned around to look at my three escorts, and noted that Clockblocker and Triumph had backed off.  It was just the PRT uniform, now.



I felt a moment's trepidation.  Was this the point where the PRT officer beat me within an inch of my life, while everyone else turned a blind eye?



``Kit, and one bundle,'' the PRT told Clockblocker.  I was surprised to note that it was a woman's voice, behind the featureless helmet.  The junior hero hurried off to the end of the hall opposite the elevator.  She wrenched me around until my back was to her, then bent down to remove the leg restraints.  Triumph stared at me, arms folded, while she did it, the threat implicit.  She removed my hand restraints as well, then handed the gear to the hero.



The officer stepped into the cell with me, and the door shut behind her.  ``Clothes off.''



\emph{Oh.  Worse than a beating, then.}



I tried to tell myself to stay calm, to not be embarrassed.  This was a combination of procedure and psychology.  They wanted me off guard, feeling vulnerable.  In the time Clockblocker had me on pause, Tagg had likely outlined orders to this extent.



I kicked off my shoes, removed my top and running pants, folded them, and set them aside.  There were no shelves, so I left them in one corner of the room.



The PRT officer undid the neat folding, rifling through pockets for something, anything, then left my clothes in a heap.



Once I had my underwear off, she checked it, then gave me my next order.  ``Glasses.''



I removed my glasses and handed them over.  She turned them over in her hands, twisted and manhandled them until I worried the frames would snap.



``Shower.  Rinse off until I say stop.''



I gave her a quizzical look, and she pointed.



I crossed the room to investigate.  Above the toilet, there was an opening in the wall, about four feet above the ground.



``Three buttons,'' the uniform said.  ``Flush, sink and shower.  Squat to use the bathroom, get on all fours or squat to shower.  If the screen flashes yellow and beeps, that means cameras are going on and someone's got something to say to you.  You'll have six seconds to finish your business and cover up.  Screen flashes red, beeps twice, it means door's opening.  Again, six seconds to cover up.''



\emph{A little inhumane}, I thought.  Would that be more psychological pressure?  Regular visits?  Interrupting my sleep?  Unreliable privacy?



``Rinse,'' she repeated.



\emph{Maybe Tagg wants me to snap and attack her}, I mused.



But I did as she'd asked.  The spray was lukewarm, and the stream was directed into the toilet, using the same drain, which made it awkward to get underneath without actually crouching in the toilet itself.  That was only compounded by the fact that the vent was still blasting in cool air, chilling the parts of me that weren't immediately under the stream.



I grit my teeth, told myself that Lung had probably dealt with it, wedging his six-foot-plus frame beneath the stream.  It would have been worse for him, being larger, blind, missing something between the legs.  Except he maybe hadn't had a guard in the room with him.  Too dangerous.



For an instant, I wished I had enough of a reputation that this woman wouldn't be there, watching me.



The door opened partway, while I stood there dripping.  She was kind enough to block the opening with her body, so I didn't flash the two young heroes.



She threw a bundle onto the bed.  A towel?  Clothes?



I started to move towards it and she barked out, ``Stop.''



Apparently I wasn't allowed to dress.  She had more things in her hands.  A tool kit.  She fished out a set of sterile gloves.  ``Allergies?''



``I'm allergic to bee stings,'' I said, trying to inject some levity into the proceedings. I couldn't see her expression.



Damn it.  I was wet, beaded with moisture, my hair clinging to my scalp, and doing my best not to shiver as I cursed the cold air that flooded the room.  I used my fingers and fingernails to comb my hair back away from my face.



``Latex allergy?''



``No,'' I said, ``And I was joking about the bee stings.''



Not even a recognition of the joke.  ``Are you on any medications?''



``No.''



``Birth control?''



``No.''  \emph{Condoms, }I thought.



``Two ways we can do this.  You cooperate, takes five to ten minutes to do a full search.  You fail to cooperate, if you fight me, bite or struggle, I step outside and we turn on the countermeasure, and then do a search while you're incapacitated.''



Her head lifted fractionally, as if she was glancing up at the electricity-dispensing orb above.



``I'll cooperate,'' I said.



Oh, how glad I was, that I could focus my power elsewhere, distract myself.



Tagg had arranged everyone in a conference room upstairs.  The heroes, suits and uniforms I presumed were key members of the PRT, and one or two more, who sat a distance away from the Director and his people.



``Plans,'' Tagg said, ``Go.''



``We bring Defiant and Dragon in,'' Miss Militia said.  ``They ship her to another PRT office where we can hold her until a trial.''



``Sensible,'' Tagg said, ``Except we expose ourselves to attack while \ldotsing her.''



``We're vulnerable to attack \emph{here},'' Miss Militia said.



``We can't act until we know what she's doing,'' another cape said.  A woman with a high collar.  Dovetail.  ``What's her plan?''



There was a silence.



``Thoughts, Miss Militia?'' Tagg asked.



``She's\ldots intelligent.  In every case we've crossed paths with her, she's proved resourceful.  She was confident and self-assured when she turned herself in.  Whatever this maneuver is, it was calculated.''



``Mrs. Yamada?'' Tagg asked one of the people in suits at the far end of the table.



``I've read up on her, studied the records you have of her, talked to the students that knew her best, for better or worse.  Greg Veder, Emma Barnes, Sophia Hess, Madison Clements\ldots her teachers, her father\ldots I'm not so convinced.''



``You disagree with Miss Militia?''



``I can't say for sure without talking to the girl, but actual surrender isn't impossible, given my understanding of her.''



``I'm not saying she's not surrendering,'' Miss Militia said.  ``I'm saying she's \emph{plotting something}.  The two things aren't mutually exclusive.''



``She could be attempting to bring down the PRT,'' Assault said.  ``Do it from within.  With the charges we have lined up against her, she can request a jury trial.  She uses that as a platform to dish out dirty secrets.  Confidential data on Armsmaster, details from records they stole from the database, the Echidna event and the fallout therein\ldots''



``Given how \emph{that's }gone,'' Dovetail said, ``She'd be digging her own grave.  We all thought the details would leak, but Cauldron's cleanup is efficient.  Anyone who \emph{tries} to leak details gets\ldots censored.''



``Killed,'' Adamant clarified.  ``Or disappeared.''



``It would be unfortunate if she were killed in our custody,'' Tagg said.  ``She'd be safer in the Birdcage.''



``With the public support she has within the city?'' Miss Militia asked.  ``Good luck getting her there without a fair trial.  There's going to be a \emph{lot} of eyes on this.''



``So she's forcing our hand,'' Tagg said.  ``The question is \emph{why}.''



``To oust \emph{you},'' Miss Militia said.



``Revenge?'' Tagg asked.



``I don't know, but I had a conversation with her a few days ago, and she said she had something in mind that she could use against you.  I didn't know what it was before now.''



``I see,'' Tagg said, rubbing his chin.



Back in the cell, I sighed.  I could see the uniform flinch in reaction.  She had her fingers in my mouth, feeling beneath my tongue and around the base of my gums.  When I didn't bite like she'd feared, she finished and removed her fingers from my mouth.  She removed the gloves, where they joined the first pair she'd donned.



Miss Militia had told Tagg.  I wasn't \emph{surprised; }she gave me the impression of someone who followed the letter of the law.  As willing as she'd been to open negotiations, she would still do what it took to keep her job and maintain the peace.



I was maybe a little disappointed.  I hadn't demanded she keep it a secret, and it wasn't liable to change anything, but it made for a small breach of faith.



The PRT officer finished off the search by combing my hair with a metal comb that I suspected was sharpened at the points to double as a wood saw.  It \emph{felt} like it, at least.  The combing wasn't done to look tidy, but to search my hair for any foreign matter or tools.  I was just glad they hadn't decided to shave it all off.  I wouldn't have put it past them.



``Towel is in the bag,'' the PRT officer said.  She shook a plastic bag to open it, then began putting my clothes inside, leaving me only the underwear.



I opened the drawstring bag, which was missing a drawstring, then sorted out the contents.  A thin towel, a single sheet so thin it was translucent, a pillow and pillowcase that looked to be the same fabric as the mattress, folded double, half the size of a normal pillow.  There were prison sweats, black, with the word `Villain' printed across the shoulders and down the right leg in white, with a white t-shirt with the same word in black.  There was a small kit with a rubbery, flexible thimble-toothbrush that fit over one finger and a small tube of toothpaste, three tampons with soap, three cardboard applicators, and three pads.



Not that it mattered.  I'd been under enough stress the past few months that I'd missed my periods entirely.  I might have panicked, if the timing of it had been different.  I was safe.  Ninety-nine point nine percent sure I was safe.



She waited until I had quickly toweled dry, put the underwear and prison sweats on, then handed me my glasses and opened the door.  I caught a glimpse of Triumph and Clockblocker before she blocked my line of sight.



``Sit tight, princess,'' she said.



The door whisked shut, leaving me confined in a space so narrow that I could lay down and touch two opposing walls with toe and outstretched hand.  Only the ceiling was out of reach.



I adjusted the sweats, leaving the front open, headed to the bed, laid down the pillow and stretched out.



``\ldotsAlcott girl,'' Tagg was saying.  ``Is she here?''



``On her way,'' the deputy director answered.



``Then I think it's time to settle on a game plan,'' the Director said.  ``I'm Skitter's target, or one of them.  \ldotsssination?''



``Coercion,'' Miss Militia said.



``I see.  Her power extends to the remainder of this building, even now, am I right?''



``Arthropodokinesis, arthropodovoyance,'' the Deputy Director said.  ``She's on record as a master eight, thinker one.  The thinker classification is key here: ex-Director Piggot noted Skitter can see through her bugs' eyes.''



``Can she lipread?'' Tagg asked.



``No idea,'' the Deputy Director replied.



``I said it before,'' Miss Militia said.  Her voice was a fraction quieter than before, but I couldn't read her tone with the bugs' hearing.  ``She's resourceful.  I'd assume she took the time to learn, if it would expand her capabilities.''



Director Tagg nodded slowly, then rubbed his chin again.  The movement of his wrist against his armrest nearly killed the bug I had in between his dress shirt and jacket.  ``Agreed.  I already informed each of my officers to treat her as though she had a two point classification in every category, or two points \emph{higher} in cases where she's already received scores.  Brute two, mover two\ldots all the way down the list.  It won't do to underestimate her.  Let's anticipate that she's put herself in this position to have full access to the building by way of her power.  Until further notice, staff aren't to access any confidential files, we don't speak on any private matters while within her reach, capes are to remain masked at all times while on the premises, and we'll devote all remaining resources to preparing for any conflict.''



Clockblocker and Triumph had entered just as he finished speaking.



``Conflict?'' Clockblocker asked.  He took a chair among the other Wards.



``It remains a possibility.  If her teammates were to attack, she'd be positioned to use her power to hamper us, up until we used the nonlethal measures to incapacitate her,'' Tagg replied.



``I could use my power,'' Clockblocker said.  ``Put her on pause, repeat the process until we have other measures in place.''



``No,'' Tagg said.  ``We need you elsewhere, and each contact gives her a chance to act against you or escape.  She's confined, and we can use countermeasures to incapacitate her if need be.''



The Director set his elbows on the table and leaned over, covering his mouth with his hands.  I missed some of what he said, as his words were muffled.  ``And \ldots her stew for a while.''



Ah.  So the psychological pressure extended another step.  A strip search, a claustrophobic cell, stripping away my possessions, and now he planned to keep me cooped up in here until my composure cracked.  Not so effective if I was being put on pause, with only a fraction of the time passing.



``The alternative,'' Assault said, ``Is that this is exactly what she wants.  She wants us to react.''



``It's possible,'' Tagg said.  ``Getting us agitated, getting media attention, having us call in assistance, only to humiliate us further.''



``You're bringing in help?'' Miss Militia asked.



``We'll see,'' Tagg said.  He touched his face as he spoke, and it muddled his words, ``In the \ldots, see to the \ldots I recommended in dealing with her.  It would be best if you didn't use your computer, with her \ldots watching--''



``No need.  I remember what we discussed,'' Miss Militia said.  ``I'll arrange it.''



``Make any and all calls outside of her power's range.''



``We will,'' Miss Militia said.



``If she's \ldots fight a war over the city's heart, let's make the first move.  We contact the media, control \ldots \ldots they have access to, make sure the first thing the public hears is our side.  Make sure we make some mention of Accord, and Hellhound's penchant for chewing up people who trespass on her territory.''



``I'll see to it,'' the deputy director said.



Odd, to be so utterly helpless while I watched my enemies maneuver against me.  I couldn't, \emph{wouldn't} use my power here.  I couldn't talk to them, or request anything.



I shifted position, and the metal bands squeaked.  I couldn't find a position to lie down, and wound up sitting.  I toweled my hair ineffectually in an attempt to get it dry.



An officer, out of uniform, appeared at the door to the conference room.  ``Media already has the story.  Vickery, with channel twelve.  He's asking us for final comments before the story goes live.''



``Is he on the phone right now?''



``Yes sir.''



Tagg stood, ``Tell him I'll talk to him when I'm done here, and I'll make any wait worth his while.''



``Yes sir.''



As the uniform left, Tagg remained standing at the end of the table.  ``Anticipate confrontation, but don't seek it out.  Whatever they have planned, they'll want to rescue her.''



``We can seal off the stairwell access with containment foam,'' Kid Win spoke up.  ``Seize the elevator, to prevent access to the cells.  If there's an attack, we shut down the elevator.  In the worst case scenario, they can't get her out before reinforcements arrived from other cities.''



``You can do it fast?''  Tagg asked.



``Very,'' Kid Win said.



``See to it.  Where do things stand with the defense system against the bugs?''



``Not done, but I could wrap it up soonish with Sere's help, maybe.''



``Sere?  You'll cooperate?''



``Yes,'' Sere replied.  ``Of course.''



``Then it's settled.  Everyone else, double the number of patrols, form pairs at a bare minimum, focus on recon more than fighting.  Track the Undersiders, meet with contacts.  Consider this a mid-to-high priority situation, keep that in mind if you've any favors to call in and you're weighing whether you should.  Miss Militia?  Ready the measures we discussed, and use the Wards.  We don't want them in a direct confrontation, and they can fend for themselves if ambushed.''



``Yes sir.''



With that, the meeting was broken up.  Tagg headed to his office, the Wards moved to the elevator to head down to their headquarters, below the cell that held me, and the Protectorate headed out on patrols.



My power's range was about five blocks.  It should have been larger, going by the running theory that feeling `trapped' extended my reach, but I was in here by my own device.  I couldn't necessarily force it.



Five blocks felt oppressively small, in the grand scheme of things.  I was in a six-foot by six-foot cell with thick walls, nothing to read, no television to watch, and only dull metal and chrome to look at.  The vague blur of my reflection in the walls was only a dark shadow, the occasional gleam of light of my glasses.



Around me, the PRT office buzzed like an anthill I'd kicked.  People were heading here and there on tasks and missions, reacting, preparing, anticipating some form of attack.  The higher-ranking members of the PRT made calls to contacts, prepared, and set security measures in place.  PRT uniforms got geared up, off-duty teams were called in and prepared, organized in defensive lines around the building.



Miss Militia, for her part, sent Flechette on an errand, instructing her to make a phone call and return as soon as possible, and then started organizing the Wards.



I set bugs on the minute and hour hands of a clock.  It was both a curse and a blessing, because it made me acutely aware of how slowly time was passing.



``Things are going crazy,'' Crucible said.



``This is big,'' Clockblocker said.



``I'm just saying, you'd think things get \emph{calmer }when the kingpin- \emph{queenpin}-``



``Crime lord,'' Clockblocker said, ``It's easier.''



``When the crime lord of the city turns themselves in.''



Vista spun around in her chair to face Crucible, ``She's probably planning something like getting put in jail, then breaking out and showing us there's no point in trying to catch her, because we can't \emph{keep} her.  And she'll do it with teeny-weeny \emph{bugs}, make Tagg look bad, maybe get him fired.''



``Fits,'' Clockblocker mused.



``But she can't know she'll escape.  What if we \emph{did} have Dragon and Defiant move her halfway across the country?''



``She used my power to cut Echidna in half,'' Clockblocker said.  ``She could deal with that, too.''



``Again with the Echidna thing,'' Crucible said.  ``Can't you tell--''



``Classified,'' Clockblocker, Kid Win and Vista said, at the same time.  Kid Win didn't even look up from the containment foam dispenser he was tinkering with.



``Fuck you guys.''



The screen in my cell flashed yellow, then beeped once, a sound loud enough that it made me jump.



I stood from the bed and walked around until I faced the screen.



It stayed yellow for long seconds, then went dark.



\emph{Checking on me?}



I sat back down.



The minutes were ticking away.  Tagg was counting on this confinement wearing on me.  Putting me in a different headspace for when he finally decided to come down and grill me.  It\ldots was working, but probably not to the degree he was thinking.  Being manhandled by the PRT officer had been another attempt at getting me outside of my comfort zone, no doubt a gambit, where any resistance from me would be met by a shout from Triumph, a beating and a use of Clockblocker's power before the door was shut in my face.  A lack of resistance only making me uncomfortable, putting me in my place, for lack of a better phrase.



But again, it didn't matter.  My concerns were on bigger things, on the space beyond this cell, on everything I needed to achieve.



A family made their way to the lobby.  I assumed them to be tourists, until the guards let them into the building.  Two adults and a young girl.  The Alcotts.



Dinah had cut her hair short.



Reinventing herself?  Distancing herself from being Coil's `pet'?



Tagg met them at the end of the lobby, then ushered them upstairs to the conference room.  They were joined by Mrs. Yamada, her cousin Triumph, and Miss Militia.



Tagg waited until everyone else was seated before sitting at the head of the table.



He pressed a key, and the monitor in my room beeped.  I lay down on the bed before the six seconds were up and the cameras went on.



When he was done looking in on me, he closed the laptop.



``She turned herself in,'' Dinah said.



``Your power pick up on that?''  Triumph asked.



``We watched the news,'' Dinah's mom said.



``When you said sending Defiant and Dragon into the school would virtually guarantee that Skitter was brought into custody,'' Tagg said, and his phrasing was odd, as if he were choosing words carefully or there was a tone my bugs' hearing wasn't picking up on, ``you didn't say anything about \emph{this}.''



I \emph{did} catch the emphasis on `this' as he finished.



``This?'' Dinah's father asked.



``That she'd surrender, nearly a week later.  The timing of it, the fact that it could be a ploy.''



``I didn't know,'' Dinah said.



``If you have an accusation,'' Mr. Alcott said, ``Say it outright.''



``I'm saying your daughter was helping Skitter, not us.  That everything seems to suggest she was aiding and abetting a known criminal.''



``Are you insane?'' Mr. Alcott asked.  The volume of his voice rose.  ``Those thoughts don't even connect!''



``I don't necessarily agree with the Director's line of reasoning, Dinah,'' Miss Militia said, ``But Skitter's a known criminal mastermind, with an emphasis on the latter.  She's a capable strategist and a battlefield tactician.  As far as we were aware, she was well situated as one of the more powerful villains in North America, judging by her control over this city.  In the past week alone, she's \ldots two villainous organizations and folded a third into her own.  There's no reason for her to surrender.  The only way any of this makes sense is if there's a greater plan at work.''



``And you think Dinah had something to do with that plan?''  Mrs. Alcott asked.



Mrs. Yamada leaned forward, ``It's very understandable if Dinah feels indebted or attached to Skitter, to Taylor Hebert.  She owes her a great deal.''



Dinah mumbled something.  I wasn't sure if it was even a word.



Mrs. Yamada continued, ``We're only trying to make sense of this.  Wanting to help someone who's done a great deal for you isn't a bad thing, Dinah, understand?  But there's other things going on.  Sensitive things.  Skitter may unwittingly do a lot of damage or put herself at risk, if she says the wrong things and the wrong people hear.''



``\ldots,'' Dinah said something under her breath.



``Beg pardon?'' Mrs. Yamada asked.



``Good.  If she does a lot of damage, then \emph{good}.''



Director Tagg started to speak, but Mrs. Yamada cut him off.  ``Why is that good, Dinah?''



``Can't say.  Won't say.''



``You \emph{are} working with her, then,'' Tagg said.  He shifted position in his chair.



``No.  Yes.  Both.  I'm working for \emph{everyone}.  I don't think Skitter's very happy with me, really.  But she's still here, because I told her to be.''



``You've been in communication with her?'' Miss Militia asked.  I could tell how much gentler her voice was than Tagg's.



``No.''



``Oh my lord,'' Tagg said, leaning back in his chair and staring up at the ceiling.  ``I think I'm about to have an aneurysm.''



Dinah didn't reply.



``Do you hate the PRT, Dinah?'' Miss Militia asked.



``No.''



``Or heroes?  Do you blame us for not helping you when you needed it?''



``No.  A little, but that's not important.''



``But you want Skitter to do damage?  To hurt us?''



``She'll do damage, one way or another.  If she didn't come here voluntarily, she probably would have become \emph{meaner}.  It would have turned into a big fight, and she would make a mistake eventually and get brought in.  But she decided to surrender, so the same thing happens.  I'm glad that happened.''



``All because we revealed her identity,'' Yamada said.



``Yes.''



``But we don't know the ramifications of this ploy of hers,'' Miss Militia said.



``I do,'' Dinah replied.  ``But I'm not telling.  And I'm charging ten times as much if you ask me for a number, and then I'll \emph{lie}, and I won't be able to use my power for a while after.  And your bosses don't want that.  Not with an Endbringer coming soon.''



``You'll charge us for a number you won't provide?''  Tagg asked.



``Yes.  Because I charge you for \emph{asking}.  I can't help but look for the numbers, so I have to look.  And that makes my head hurt if I do it too much.''



Tagg let his hand drop to the table with enough force to make a noise and make the lid of the laptop in front of him clatter.



``Why, Dinah?'' Miss Militia asked.  ``Why do this?''



``For everyone.  Because we got this far, it makes the numbers a little better.  Whatever happens from here on out, it makes the end of the world a little less bad.''



``A little less bad,'' Triumph echoed her.



``But it still happens,'' Tagg said.



``Almost always.  The world ends, in two years or in fifteen or sixteen.''



Tagg opened his laptop, ``Do you have anything to say to Skitter?''



``No,'' Dinah said.  ``I'm done.''



``Done.''



``Yes.  I'm busy.  It's only because my cousin works here that I even came.''



``You seem to be playing a dangerous game,'' Tagg said, ``Testing our goodwill, manipulating us for your own ends.''



``\emph{Everyone's} ends, and I didn't manipulate you.  You asked for a number, I gave it.''



He ignored her.  ``Helping her when you should be helping us.''



``I don't \emph{have} to help you,'' she said.  ``I'm not a good guy.  I'm not a bad guy.  I'm \emph{done} working for other people, answering their questions when I don't want to.  I work for \emph{me}, and for \emph{everyone}.''



Odd, to think how much time I'd dedicated to Dinah, and how little I really knew her.  There was this, only now, and the discussions we had prior to me taking her home.  So little.



Tagg was rubbing his temples.  ``Fine.  Now, when you said that the outcome of this improves the numbers, I understand that includes sending her to the Birdcage?''



``When I said I was done, I meant it,'' Dinah said.  She pushed her chair back.  Her parents joined her, standing.  ``You want more answers, get in contact with my dad, he'll let you know my rates.  They change every day.''



``Not a wise business decision for a rogue starting out,'' Tagg said, without rising from his chair.  ``Offending an organization like the PRT, a young lady like you mouthing off.  We could cooperate, instead.''



He was \emph{threatening} her?  I clenched a fist.



Dinah looked back at him.  ``I don't think you have any \emph{conception} how valuable my answers are.  I could answer one question a week for people in Asia and I'd be set for life.  I don't care if I offend you.''



``And you don't care about your savior, locked away in that cell?'' Tagg asked.



Dinah stopped in her tracks.  ``Are you threatening Taylor?''



``I don't know,'' the Director said.  ``You said she'll do damage in some form.  Maybe we need to stop that from happening.  And you said that no matter what happens, the outcome's more in our favor than it was before she surrendered.  Why?  Is it that important to remove her from Brockton Bay?  To unseat her from her throne?''



``I'm not answering any more questions.''



``You'll answer what I ask you to answer,'' Tagg said, ``Because we need to go into this with our eyes open.  We can't have Skitter damage \emph{us}.''



``Director,'' Mrs. Yamada said, ``This isn't constructive.  The last thing she wants--''



``The last thing I want is another arrogant dickface telling me what to do,'' Dinah said.  ``You want answers, Director?  Fine.  Twenty two point eight one three percent chance you die painfully, over long, slow minutes or hours.  Maybe soon, maybe in twenty years, but it'll bring you to tears, and you'll wail in pain.  That's a freebie.  Want more details?''



``Guys,'' Miss Militia said.



``You assume I care about that,'' the Director said.



``You will.''



``Guys,'' Miss Militia said, louder.



``If you refuse to give us assistance, and people get hurt, then that's on your head,'' Director Tagg said.



``I deal with that every day,'' Dinah said.  ``I'll cope.''



``Guys!''  Miss Militia stood from her chair, the feet screeching against the ground.  She raised her voice another notch.  ``Look.''



She pointed at the window.



I moved my bugs to check for whatever it was she was pointing at, then stopped.



She was pointing at the \emph{bugs}.  They'd reacted to my irritation, and were swirling just beyond the window of the conference room, clustering on the glass surface.



``Is she making a move?''  Tagg asked.



``No.  They're\ldots just there.  Reacting,'' Miss Militia said.  ``To this.  Here.''



``She's watching,'' Tagg said.



``Watching what?  There's nothing to look at,'' Miss Militia said.  ``Think about it.  What this is to her.''



``She hears,'' Mrs. Yamada finished the thought.



I shut my eyes, swore under my breath.  I'd let my guard down.  I'd been too focused on what was going on inside the building, letting bugs cluster on the outside, that I'd given my reactions away.  So much for gathering intel.



Tagg faced the window, no doubt staring at it, at the bugs.



``Arthropodaudience,'' Miss Militia said.  ``She's fully aware of everything that's been going on in this building.''



``I'm gone,'' Dinah said.  ``I can't communicate with her or the numbers change.  I'll be letting the PRT know you pissed me off.  They can expect prices to go up five percent from here on out.''



With that, Dinah was gone, saying something to her parents that I couldn't make out.



My focus was more on Tagg.



``So,'' he said, his voice low, ``You can hear me.''



``\emph{Yes},'' my bugs replied, speaking throughout the building.  They were distributed evenly enough that it would barely be audible.  A thin, almost imperceptible sound.  More than a few people jumped in reaction to it.



``I see,'' the Director said.  ``You tipped your hand.''



I didn't have a response to that.  I \emph{had}.



He turned to Miss Militia.  ``See that Kid Win gets the defense system online sooner than later.  I'd like this building cleared of bugs.''



``I'll talk to him.''



``And \emph{you},'' the Director said.  I was getting used to his voice.  I caught the emphasis there.  ``You stay put and be good.''



I shifted position, sitting on the end of the bed, elbows on my knees, staring at the floor.



Waiting, listening, watching.



Another twenty minutes, forty minutes, sixty minutes passing, with irregular check-ins by way of the monitor.  Every member of the PRT was set in place, some near the PRT headquarters, others elsewhere in the city.  Heroes went on patrol and came back, making short trips, no longer than half an hour each.  Each hero in a pairing took turns reporting to Tagg.



Rachel had been seen crossing the city earlier, as had Grue.  A meeting at the Forsberg Gallery.  If they were following Tagg's orders, there was now a PRT wagon stationed nearby, ready with a containment foam turret, in case the villains decided to meet there again.



Miss Militia got a list of phone calls to make from Tagg, then left, exiting my range.



Another half hour.  Another check-in, a group of four heroes teleported in, Miss Militia returned and whispered back and forth with Tagg.  There was a long discussion between the new heroes, Assault, Miss Militia and Tagg about how concentrated the forces were, now.  Too many PRT uniforms and heroes in one place, the danger if they were all wiped out.



In a matter of minutes, they'd organized another distribution.  Expanding control over the area, keeping two major groups out of my reach.



Only five minutes after the groups had departed, Kid Win activated his system.  Floating drones started to roam the PRT headquarters, each no larger than a toaster, each with multiple settings that they rotated between.  They emulated Sere's power on a low enough level to kill bugs in the area without doing undue harm to any people, then became laser turrets, firing an invisible beam every second for about a minute, killing a bug with each shot.  Then they shifted focus and accelerated, veering to a different location with unpredictable trajectories.



Kid Win was making more, too.  He was joined by one of the heroes that had just arrived.  Another tinker.  I caught a snippet of what they were talking about before the next drone kicked to life and killed the bugs I had on the new arrival.  Workshop talk.  Improving designs.



\emph{Damn tinkers}.



Avoiding the drones became something of a game, occupying my attention to the point that I was still able to keep tabs on a few important people, but I was badly limited in terms of my ability to listen in.  Fifteen minutes passed without me seeing or hearing anything significant.  The monitor flared yellow for another check-in.  Two minutes later, there was \emph{another}.  Irregular, unpredictable.



As a plus, Tagg seemed to be getting restless, if the movements of his blurry form within his office were any indication.  He'd arranged his forces, and the only thing he could do now was wait.



We were \emph{both} waiting.  Both biding our time in the hopes that the other would crack first, make the first move and initiate conversation.



Miss Militia left to make another batch of calls outside my range.  She returned sooner than before, made a beeline straight for Tagg, and exchanged a few more whispered words.



Together, they made their way to the elevator.  The Protectorate tinker that had just arrived was sealing off the staircase, and there was only one way down.



As a pair, Miss Militia and Tagg walked down the length of the hallway, stopping outside of my cell.  I combed my hair out of my face, squared my shoulders and faced the door.



The screen turned red.  A matter of seconds later, the doors slid open.



``Flechette?'' Miss Militia asked.



\emph{Flechette?}  Had my allies done something?



``Did you plan this?'' Miss Militia asked.



I elected not to answer.  This was a small victory, no matter what they were referring to.  Tagg had broken first, had come to me more on my terms than his.  I was going to play it for everything it was worth.



I met Tagg's glare with a level stare of my own.



``If you used Regent to make this happen--'' Miss Militia said.



\emph{Regent?}



``Not Regent,'' I said.  \emph{I hope it's not Regent}.



``You're admitting you planned her defection, then?''



Defection?  I thought of Parian.



``I\ldots left the door open for it to happen,'' I said.  True, though not nearly to the extent I was implying.



``And this plays a role in your greater plan?'' Miss Militia asked.  She was doing all the talking, here.  It seemed Tagg didn't want to break the silence.



I thought for a second.  ``Consider it symbolic.''



``Of?''



I smiled a little, then shrugged.



That seemed to be the point where Tagg lost his cool.  He didn't get \emph{angry}.  Instead, he merely said, ``Interrogation room B.''



Miss Militia held a pair of ordinary handcuffs in one hand, a taser in the other.  I turned and extended my hands behind me, and she set the handcuffs in place, holding my arm as she led me down the length of the hall, around the corner and into a large room with only a table, a chair, and more sheet metal covering everything.



``One o'clock,'' I said, when I'd taken my seat.  Miss Militia was unclipping my cuffs, moving my hands around in front of me to slip them through the reinforced table.



``I think it's about one,'' Miss Militia said.



``Exactly one,'' I said.



``Is the time important?'' she stepped away from the table.



``Her friends will move to attack at a set time,'' Tagg said.  ``She won't share that time, because she wants us to squirm, to be on high alert.''



``Eight thirty,'' I said.  ``Sunset.''



I could see his heavy eyebrows rise in mild surprise.



``You planned something for eight-thirty?''



``No,'' I said.  I smiled a little, looking down at the table.  ``I didn't plan anything.  I didn't say goodbye.  I walked away, and I turned myself in.''



``You're acting like that's something special,'' Tagg said, leaning against the wall by the door, his arms folded.



``The only instruction I gave was to Tattletale, to hold the others back until sunset, and to give them direction when they do act.  They'll have time to get angry in the meantime.  They'll be mad at me, but they'll take it out on \emph{you}.  You have to understand, even at my worst, even when I'm as mad as I was the other night, when you'd outed me, I was \emph{sensible}, \emph{reasonable} in terms of how I dealt with you and held back.  Now you get to see how \emph{unreasonable} the rest of the Undersiders can be, without me to rein them in.''



``I thought this might be it.  A lesson in the role you play here.  Leading us to think that we \emph{need} you,'' Tagg said, ``To keep \emph{them} in line.''



``That's not it,'' I said.



``No?''



``It's not even secondary, in terms of what I'm looking to achieve.  I don't think I could go back to them and return to my position if I wanted to.  And I don't.''



``Then what?'' he asked.



``It's a time limit.  You saw what we were willing to do to Butcher, to Valefor.  Even with that, even \emph{there}, we were holding back as a group.  Trust me when I say that I know my friends.  If you stand between them and me?  If you hurt me?  They're going to go \emph{thermonuclear} on you.  On the PRT as a whole.  Tattletale will make sure of it.  She'll keep them on target, guide them, and maximize the damage.  She'll \emph{do} most of the damage.''



``You said you weren't going to do any harm to the PRT,'' Miss Militia said.



``If things go that way,'' I said, ``It's because the \emph{PRT} is hurting the PRT.  Which wouldn't be an isolated incident.''



``Cute,'' Tagg said.



I met his eyes.  ``I'm just saying.  It's really up to you guys.  Send me to the Birdcage, you lose everything.  Things get ugly for the PRT at a critical point in time.  I suffer, the Undersiders suffer, \emph{you} suffer, the world suffers.''



I stopped, watching him for any sign of doubt, for a waver in his eyes, for a change in his expression or posture.  His poker face was good.



Miss Militia shifted position, but didn't speak.



``Or?'' Tagg finally asked.



``Or you let me call my lawyer, and then you hear my demands,'' I said.



``Demands?'' he growled the word.



``Demands.  I have several conditions you guys will have to meet before I capitulate.  I'll bow my head, appear in public, plea bargain, do whatever you want.  You get \emph{me}, wholesale, no contest, and no complications.  The \emph{PRT} gets a victory at a point in time when, like I said, it's most vulnerable.''



I studied his expression, then looked at Miss Militia.



``It's your choice.  You won't like my demands.  They call for big changes.  But the alternative is an all-out war.  I think Miss Militia will agree with me here, if the PRT doesn't hear me out, it deserves what it gets.''





