





Miss Militia handed me a phone and uncuffed one hand from the table.  I dialed the number I'd memorized and waited while she and Director Tagg watched.



``\emph{Mr. Calle, Esquire,}'' the voice on the other line said.  He sounded distracted, and the voice was slightly muffled.  I could hear noise in the background, voices.



``It's time,'' I said.  ``I'm at the PRT headquarters, second basement floor.''



``\emph{Ms. Hebert!  Excellent!  I was just telling myself that I'd almost run out of things to see in your city, here, and was about to let myself start being concerned for your welfare if it got much later.  I'm in your territory as we speak.}''



``My territory?''



``\emph{Getting a sense of who you are as a person and a personality.  There's a number of people here who are very concerned for your welfare.  They don't quite believe me when I say I'm looking out for your interests.}''



``Okay,'' I said.  ``Big guy?  Beard?''



``\emph{A young lady, dark-haired.}''



I thought for a second.  ``Tell her `fly in a paper box.'''



He didn't cover the mouthpiece of his phone as he spoke the phrase.  There was a pause, then Mr. Calle spoke into the phone once again, ``\emph{That did it.}''



\emph{I don't really care}, I thought.  I just didn't want him getting in any trouble.  ``How soon can you be here?''



``A five minute drive.''



``It's not a five minute drive from there to here.''



``I'm a fast driver.  No need to worry, but\ldots maybe don't mention it to the law enforcement officials that are looking over your shoulder.  Do you have any preferences for donuts?  Coffee?''



There was a murmur on the other end.



``Someone's telling me you want tea,'' he asked.



``Just-'' \emph{Just get here}, I was about to say, then I reconsidered.  I knew where he was, and I was tempted at the thought.  Besides, I knew Tagg was watching me.  ``A BLT on toasted white and a sugar donut.  And tea.''



``They don't sell any tea here, but I'm sure we can contrive to get you some in a timely manner.  I trust you haven't said anything to the glowering heroes?''



``No.''



``Excellent.  Keep your mouth shut, now.  I'll be there in six.''



With that said, he hung up.



``A sandwich, donuts and tea,'' Tagg said.  He had his arms folded.



I smiled a little, but I didn't reply.



``Very casual,'' he mused.  He took the phone, gripped my wrist in his hand and set the handcuff back into place.



I shifted position, and the movement raked the chain of my cuffs against the ring that held them fixed to the table.  It was hard to get comfortable.  The table and chairs were bolted to the floor, and my hands were held in front of me.  I got the impression the setup was meant for villains just a touch taller than I was – I couldn't quite lean against the chair back without the cuffs cutting into my wrists.



``I'm trying to figure you out,'' Tagg said.



I ignored him.



``My aims aren't very high.  I'm not a psychologist, like Mrs. Yamada, I'm not experienced in the ins and outs of the traumas you capes go through or the damage that shit causes.  You and I haven't really squared off yet, like you have with Miss Militia.  Those two understand you on levels I never could.''



I glanced at Miss Militia.  Her expression was inscrutable behind the stars-and-stripes scarf she wore over the lower half.



``I'm setting my sights lower than that.  I'm trying to figure out if you really think you have the upper hand, here, if you're arrogant enough to expect everything will go your way\ldots'' Tagg paused, studying me, as if looking for a response.  ``\ldotsor if you intend to martyr yourself.  Is that the idea?  You go to the Birdcage, but you make some demands first?''



I would have put my head on the table and tried to close my eyes for a minute, but the setup wasn't very accommodating.  I didn't want to try to then realize I couldn't get comfortable.



``Maybe you don't really \emph{get} what the Birdcage is.  See, I hate it.  I was in Lausanne in two-thousand two through oh-three.  Fought a whole mess of ugly.  People that couldn't be reasoned with, people who were hopeless, in the grand scheme of it.  Victims, as much as anyone else.''



I found myself listening, despite myself.



``We shot them, the people who heard too much of the Simurgh's song, who weren't just walking disaster areas, but who'd listened long enough that they \emph{lost} something.  Men, women and children missing that moral center that people like Miss Militia and I have.  Hell, even \emph{you've} got morals.  They didn't.  I'm sure you heard about it, you're not \emph{that} young.  Suicide bombers, dirty bombs.  \emph{Terrorism}, if you will.  Eleven year olds and old men making their way to Amsterdam or London and opening fire in a crowded area.  Just like \emph{that}.''



Tagg slammed his hand down on the metal table, coinciding with the `that'.  I jumped a little, despite myself.



\emph{He's just trying to rattle me.}



``Once we realized what was happening, we had to act, contain the damage.  Contain \emph{families}.  Had to act against people who went home from a day of trying to kill the rest of us and cooked a nice dinner, oblivious to just how fucked they were in the head.  People who were otherwise \emph{good, }who got warped on a fundamental level, left open to the preaching and the incitement of their angrier neighbors.  Two years of fighting before we got the word down from on high, that they couldn't rehabilitate the ones they'd captured, the ones who'd listened too long.  The poor assholes would play nice until they saw an opportunity, then they'd take it, do as much damage as they could.  Two years fighting good people who'd been convinced they had to throw their lives away fighting an enemy that didn't exist.  So we closed the perimeter, bombed them out, herded them and gunned them down.''



I glanced up, briefly meeting his eyes.  The lines around them seemed just a little deeper.  I wasn't sure if it was emotion, memories coming to the surface, or if it was just the lighting in this interrogation room.



``Which takes me back to my original point,'' Tagg said.  ``The Birdcage.  I hate it.  Hate what it stands for, the affront to our freedoms.  The \emph{farce} of it.  You know what that word means, little girl?  \emph{Farce}?''



I almost took the bait and responded, bit my tongue instead.



``Guess not.  And Miss Militia said you were smart.  When it comes to the monsters and the menaces who are more trouble than they're worth, I wish with all my heart that we had another option.  Look me in the eyes, now.  I want you to see I mean what I say.''



I met his eyes.



``I'd rather do what we did in Lausanne than use the Birdcage.  End result's the same.  You're gone from this world.  It's more \emph{merciful}, understand?  If it was legal, if I got the okay from on high, I'd make you kneel in the center of this very room and end you with one well placed bullet.  Better than you getting in a van and getting \emph{disappeared}, dropped into a pit that some of the scariest, meanest capes around haven't figured out how to escape, a literal hell on earth.''



\emph{Disappeared}.



``But as much as I hate the Birdcage, I'll gladly use it if it gets menaces like you off the streets and out of the way of civilized Americans who are trying to live their lives.  And my bosses know that.  They know I'm just as stubborn as the worst of \emph{them}, because I've fought bastards like the sad souls in Lausanne, who didn't even know \emph{how }to yield, and I outlasted them.''



I wasn't sure I could have responded if I'd been willing to open my mouth.



``I want you to think on that.  As much as you see me as an asshole, maybe you look down on me because you think you're smarter than I am, but you think about what it means that I'd sooner shoot a misguided sixteen year old girl than send her to that place\ldots and I'd sooner send you there than let you go free to keep perverting the system.''



``My lawyer's here,'' I said.  I could sense him, striding through the lobby to talk to a receptionist at the front desk.  ``Mr. Calle.  He's upstairs.''



``Someone will show him the way down here,'' Tagg said.  ``You and I, we can keep chatting here.''



I shut my mouth, frowning.  Miss Militia wasn't acting, wasn't saying a thing.



``I wonder if you realize what you've really done.  Pulling the shit you have in this city.  Forget the PRT, forget me and the people I work for.  Let's talk about the grander perspective.  The \emph{precedent} this shit sets.  You know there's already been others who tried to do what you're doing?  Take over?''



\emph{People have been trying to take over for a long time, }I thought, but I didn't say it aloud.



``People are getting hurt, \emph{hurting others}, trying to follow in your footsteps.  You're a fucking \emph{pioneer}, aren't you?  Do you get that?  That part of what we're doing, here, is not just stopping \emph{you}, dealing with you Undersiders, whatever your excuses might be.  It's the effects that reach across this entire \emph{country}.  The \emph{world}.''



I didn't reply.  My focus was on Mr. Calle, who was making his way downstairs in the elevator, accompanied by the same PRT soldier who had taken me to my cell.



``What's the name of the fellow who tried to take over that town in Alaska just a few days ago?  You remember, Miss Militia?''



``Hiemal.''



``Hiemal.  How many did his people kill?''



``Three.''



``Three dead,'' Tagg said.  He pulled a chair away from the table, set one foot on it, so he was looming over me.



Mr. Calle appeared in the doorway.  I'd looked him up prior to first contacting him, and I'd seen his photos online.  I was caught off guard, nonetheless, on two very different fronts.



``Good afternoon,'' he said, putting his briefcase down before extending a hand to Miss Militia, smiling in a way that showed off his very white teeth.  I'd assumed that his prim appearance in the pictures had been because he'd been anticipating having his photos taken, or because he'd been appearing in public.  His black hair hadn't just been cut, it had been \emph{styled,} his eyebrows shaped.  He had long eyelashes, I noted, and a small cleft in his chin.  He was an exceptionally handsome Latino guy, in a light gray suit with a white vest beneath, and a red tie.  He had a folder and a paper bag under one arm, in addition to the briefcase he'd put down.



His immaculate appearance was the first thing that caught me off guard, and it set a stark contrast with the corner of one nostril and one of his cheekbones, where, apparently, one of his clients had done some damage.  It was a cut, but puckered around the edges where it had been burned, either with fire or some kind of acid.



He extended a hand to the Director, who glowered but shook it.  He flashed another white smile at Tagg, ``Quinn Calle, I-''



``I know who you are,'' Tagg replied.



``Excellent.  That should make the rest of this easier.  I'd like some time alone with my client.  I already have the bulk of the paperwork, but if you could give me anything that came up in the last short while, I'd appreciate it.''



``I'll see what we have,'' Miss Militia said.  She and Tagg turned to leave.



Calle brushed the seat clear where Tagg had stepped on it, then sat down just to my left.  ``And Director?''



Director Tagg paused in the doorway.



Mr. Calle pointed at the one-way mirror at one side of the interrogation room.  ``This is a \emph{confidential} meeting with my client.  I would \emph{never} imply that anyone in the PRT would be so crass as to listen in, but\ldots let's leave that room empty until further notice, okay?''



Tagg visibly bristled at the implication.  Wordless, he turned to leave.



``And cameras stay off!'' Mr. Calle called out at the Director's back.



Tagg shut the door with a little more force than necessary.



``Ms. Hebert,'' Mr. Calle said, without looking at me.  He set the folder on the table and began sorting out the contents.  He waited until the paperwork was all arranged in front of him before he turned his attention to the paper bag, retrieving my sandwich, a small carton of six donuts, and a small thermos.  He met my eyes and spoke, ``We finally meet.''



Again, that smile, the kind of smile someone could only really give if they were attractive and they knew it.  He didn't seem to mind the blemish on his face, acted as though it weren't there, as if that dictated how others would react to it.



``Can we cut out the charm and get to business?'' I asked, as I reached for the thermos and sandwich.  ``There's something of a time limit.''



The smile dropped from his face, and he was all business.  ``A time limit.  Can I ask?''



``It's twelve past one,'' I said.  ``We have until eight-thirty.''



``Very well.  Let's get moving.  First off, I want to get some things clear.  I'm an excellent lawyer, I've worked with more than a few big-name villains, as well as heroes who went astray.  I have the rest of my firm backing me, and their talents are but a phone call away.  \emph{But.}``\emph{  }He paused in a very deliberate way.  ``You should know that I'm not the lawyer you want at a jury trial.  We've run simulations, and I don't sell when it comes to juries.  This little mark is a good part of that.''



He touched his face, where the scar was.



Mr. Calle continued, ``If it comes to a serious trial, I'll take the backseat and one of my senior partners would represent you.''



``Okay,'' I said.  ``That's fine.  I don't want this to go to trial.''



``Alright.  We can work with that.  In the meantime, let's see what we're up against\ldots''



He turned the first page in one of the neatly bound sheafs of paper.  ``Charges\ldots chime in, but don't panic, alright?''



``Okay,'' I said.



``April tenth, criminal negligence with a parahuman ability, sixteen charges of assault, sixteen charges of battery with a parahuman ability.''



I tried to think.  April tenth?  Early in my career?



``Lung,'' I said, ``I attacked him and his gang.  They're seriously charging me for attacking Lung's henchmen?''



``They're going to charge you with everything they think they can get away with and see what sticks.  Depending on who they could actually \emph{find} and convince to testify, they'll drop charges after the fact.  We can maybe use that, or we \emph{could}, if circumstances were different and we were wanting to take this to trial.  No need to worry.  Gut reaction?  Could they make it stick?''



``The Lung part, yes, but the rest\ldots probably not.''



``Okay.  Let's run down the list.  April fourteenth.  \emph{Thirty two} charges of willful felony assault with a parahuman ability.  Thirty two charges of \emph{hostage taking}, technically domestic terrorism, each perpetrated with a parahuman ability.  \emph{Robbery} with a parahuman ability.  Willful damage to government property.  Disturbing the peace.''



``The bank robbery.  I didn't damage any property.''



``Right.  April twenty-fourth?  One case of battery.''



``I don't remember that.''



``An\ldots Emma Barnes.  She appeared-''



``Right.  No, I remember what that was.  It happened, didn't think anything would come of it.''



``One of the girls who bullied you.  Odd that they took their time filing charges on it.  Only this past week.''



\emph{Tagg must have talked to her}.  I shrugged.



``Moving on, then.  Incidents taking place at the\ldots Forsberg Gallery, May fifth.  Five cases of assaulting a law enforcement officer.  Five cases of \emph{battering} a law enforcement officer, three performed with a parahuman ability.''



``That's attacking the heroes?''



``No.  That'd be an entirely different charge, and\ldots'' my lawyer flipped through the papers, ``Just double checking\ldots there's a conspicuous lack of charges involving your altercations with major heroes.  It could be that they discussed it and didn't feel it necessary.  Things get complicated when capes take the stand, given the issues of identity and character, and they might not have wanted to dredge up old business.  If not that, the only way I could imagine it is if the heroes in question withdrew all charges?''



He pitched his voice to make the statement into something of a question.



I thought of Armsmaster.  Him?  Maybe.  But Assault?  Miss Militia?  That was harder to picture.  The Wards?  Harder still.



``I don't know which it is,'' I admitted.



``All right.  Something to look into, if we have time.  Still on May fifth, \emph{eighty-one }charges of willful felony assault.  Still at the fundraiser.''



He raised one eyebrow.  I only nodded confirmation.



``Skipping ahead a month to June third, we've got\ldots complicity towards one count of kidnapping using a parahuman ability.  This was-''



``Sophia Hess.''



``One of the girls who bullied you.  Extenuating circumstances, perhaps,'' he said.  He made a note in the margins of the document.  ``June fourth, you're supposedly complicit in class two extortion with a parahuman ability, criminal negligence with a parahuman ability and false imprisonment with a parahuman ability.''



``They\ldots can probably make that stick.''



``June \emph{fifth}.  Treason.''



``Treason.''



``That would be, in effect, declaring war against the government of the United States of America.''



``That's not what I did.''



``It's what they're going to \emph{say} you did when you took over the territory.  I'd expect they already have strong arguments lined up on that front.  On the same day, \emph{thirty} cases of assault and battery.  Six cases of aggravated assault with a parahuman ability.''



I nodded.



``June eighth, eight cases of assault with a parahuman ability.  June ninth, we've got twelve more.  June tenth, three cases of assault with a parahuman ability, one case of assault in the third degree.''



``Alright,'' I said.



``Thirteenth, we have three more cases of assault with a parahuman ability.''



``Makes sense.''



``Sixteenth of June, disturbing the peace, property damage.''



I nodded.  The days were starting to blend into one another, to the point that I wasn't sure I could guess which charges were referring to which events.



``Seventeenth, five charges of assault and battery.  One charge of aggravated assault with a parahuman ability.  One charge of criminal extortion.''



``Attacking the mayor,'' I said, almost relieved to be able to pinpoint the crime in question.



``And his family, it seems.''  Mr. Calle paused, then paged through the rest of the pad.  ``June eighteenth.  Destruction of government property, four counts.  Hostage taking, assault and battery of a law enforcement officer.  June nineteenth, complicity in another count of treason.  Complicity in manslaughter, nineteen counts.''



I nodded.  \emph{Dragon and fighting in the debate}.  Given Dragon's response in the cafeteria, I'd almost expected her to drop any charges involved in the destruction of the suits she'd sent against me.  Maybe people higher up than her had charged me anyways.  Then there was the manslaughter.  ``Apparently the murders were staged.''



``We'll have to look into that.  And\ldots that's the last we have in our actual records.  The PRT was slow in sending us the rest, but Miss Militia should deliver it soon.  There's been more in the last week, I take it?''



``More assault and battery,'' I said, feeling a touch weary.  ``Whatever charges come up with the thing at the school.  I sort of arranged to have a psychopath kill herself.  Um.  However you'd charge putting maggots in someone's eyeballs.  In self-defense.''



He didn't even flinch at that.  ``I see.  And any other charges that might catch us by surprise?''



``Premeditated murder,'' I said.  ``Of a law enforcement officer.  Miss Militia knows, but she's kept quiet on it.''



``I see,'' Mr. Calle said.  He frowned briefly.



``It was Coil.  Director Thomas Calvert was Coil.''



``Alright, then,'' Mr. Calle said.  He met my eyes, then smiled.  ``Believe it or not, I've handled worse.''



I wasn't sure if I should feel relieved at that.



``Now let's talk about our goals.  For the record, if we took this to trial, I think we could knock off most of these charges on a lack of evidence and degrees of amnesty surrounding your participation against the various class-S threats.  They're going to want to put together a jury that \emph{hasn't} heard of you, which would be difficult.  To those people, it's going to sound downright preposterous that a sixteen year old girl is being charged with treason and terrorism, especially after we reduce the number of assault and battery charges to single digits.''



``I don't want a jury trial,'' I said.  ``I've said this twice now.''



``I know,'' Mr. Calle said. ``Hear me out.  I'm wanting to make sure our expectations are realistic.  Theoretically speaking, I think we could get you charged as a minor.  Paint a picture of a bullied teenager pushed to the limit, caught out of her depth and, following the Leviathan attack, ensnared in an ugly situation where she's trying to protect people and the heroes are being unreasonable in how they interact with her.  We could \emph{use} the unwarranted unmasking to indicate just how aggressive and ruthless the PRT has been in regards to you.''



``And if I decided to plea down, in exchange for certain considerations?''



``We can still reduce the charges, which would help reduce the penalties you'd face, but where I'm confident we could get you off in a trial by jury, you'd face some consequences if you insisted on taking this route.''



``Alright,'' I said.  ``I can live with consequences.  In terms of holding them to the terms I stipulate, is there any way to set it up so they can't change their minds after they've gotten what they want from me?''



``We can prepare a contract, but that only imposes financial penalties,'' Mr. Calle answered me.  ``The PRT could theoretically get it thrown out of court, and that's ignoring the possibility that you could be sent to the birdcage.  It would depend on the penalties you're able to levy against them\ldots''



He trailed off.



I thought of Tattletale.  ``I think I have some ideas.''



``Excellent.  But the best way, I'm thinking, is to make it all common knowledge.  Let the rest of the country hold them to it.  It would depend on whether we could share the details with John and Jane Q. Public.''



``Can we talk about the terms, then?'' I asked.



``We can.  I got the impression you were able to tell time?''



``It's one twenty-seven.  Six hours and three minutes left.''



``Right then,'' he made a pained expression.  ``A good thing I told my wife I wouldn't make it to dinner.  I'll get a few of my coworkers on the line.  They can pitch in and put an intern to typing things up while we hash this out.  You don't have much ground to stand on, but we can make the legal ramifications as ugly as possible for them if they throw you under the bus.''



\sectionbreak



It took one and a half hours, roughly, to get everything worked out and organized.  After that, I had to put up with twenty minutes of waiting while Mr. Calle's law firm typed it and emailed it to us.  It took ten more minutes for my lawyer to run to a nearby print shop and get the paperwork we'd put together.  Mr. Calle then insisted on reading the entire thing through.  The wait was almost intolerable.



Fifteen more minutes passed as he went through it page by page, with agonizing slowness.  I winced a little every time he stopped and went \emph{back} to check earlier details against whatever it was he was reading.



``It's bare bones,'' he finally said.



``I didn't expect much else,'' I said.



``We could have done better with more notice, I have to say.''



``Too many variables to lay anything out ahead of time,'' I said.



``Very well.  Let's bring them in.''



More minutes ticked away as we waited for the others to arrive.  Director Tagg, the Deputy Director, Miss Militia, Clockblocker, and Mrs. Yamada\ldots they were gathering in force.  Tagg took a seat opposite us, Miss Militia to his left, his second in command to his right.



``Let's hear it,'' he said.



Mr. Calle stood, then walked around the table, handing each person present a copy of the document.  I was the only one who didn't have one in front of me.



``My client, Taylor Hebert, is offering official surrender to the PRT, for a select handful of crimes.  This surrender and an admission of guilt would be televised locally, nationally and possibly internationally, dependent on which outlets were prepared to cooperate.  In exchange, my client, Taylor Hebert, known by the alias `Skitter', requests some concessions from the Protectorate, PRT and Wards.''



``Televised?'' Tagg asked.



``It serves as insurance for my client, and it serves to signal the Undersiders to stand down, should they be considering any sort of aggression for the capture of their leader and friend.''



``Right,'' Tagg said.  ``Let's pretend she didn't plan for that.  Go on.''



``To begin with, the remaining members of the Undersiders will be given leniency for past crimes.  With the understanding that the Undersiders are serving to police this city's underworld where the Protectorate is unable, the group would cease to be the target of any aggression or harassment on the part of the PRT, Protectorate or Wards.  This fact would not be disclosed to the public, but would serve as a truce to allow both sides to carry out their respective duties in the service of Brockton Bay.''



``You're kidding me,'' Clockblocker said.



``You want us to \emph{play nice},'' Tagg said.



I watched Miss Militia.  We'd already discussed this point.  I'd gauged her response.  Now I was putting it out there in simple, clear terms, making it official.  I couldn't be sure if she'd hold to her word or if it would collapse under the bureaucracy.



I'd tested her once, and she'd informed Tagg of what I was planning.  This would be a second test, of sorts.



``Special allowances,'' Mr. Calle said, ``Would be made for crimes committed in the future, within specific limits detailed on page three of the paperwork you have in front of you.''



``You want to neuter us,'' Director Tagg said.  ``Stop us from policing the criminals who run this city.''



``As my client phrased it, Director, we're hoping to \emph{free} you to focus your efforts on real targets.''



``You can want it and begin again,'' Tagg said, ``But I won't stand by and watch it happen.''



``Quite alright,'' my lawyer responded.  He flashed a smile, ``I expect that's why Ms. Hebert has asked that you\emph{ retire, }Director Tagg.  Her colleague, known by the alias Tattletale, has apparently confirmed that you've put in the requisite number of years.  You could collect your pension without issue.''



I watched as Tagg leaned back in his seat.  He gave me a smug look.  \emph{He thinks he got to me}.



``You're dangerous,'' I said.  ``You've got a soldier's mentality at a time when we need \emph{peace}.  You'd let the world burn to\ldots give me a bloody nose.  You said it yourself.  You're unyielding, and we need compromise.''



``A reality that Ms. Hebert feels Miss Militia would be better equipped to accommodate,'' my lawyer added.  ``That's our third term.''



There weren't any retorts or rebuttals from the `good guys'.  Instead, they exchanged glances across the table, everyone looking between Miss Militia and Director Tagg.



``The PRT is led by \emph{non-}capes,'' Miss Militia said.



``That can change,'' I said.  ``Nearly a week ago, you and I had a conversation.  We talked about the issues within the PRT, the fact that you had to kowtow to non-capes and all the problems that posed.  I think the non-capes who tend to find powerful positions in the PRT are getting there by dangerous roads.  They tend to have backgrounds with the police, military, and anti-parahuman strike teams.  It sets up a combative mindset, where we don't need one.  With a cape in charge of the local team, at the very least, I could hope that there'd be a shared perspective.''



``You think Miss Militia would be easier to manipulate,'' Tagg accused me.



``I think she's a no-nonsense type.  I know she's a respected cape, that her power\ldots it's not one you want to cross paths with, so there'd be little doubt she could put up a fight if it came down to it.  And she \emph{listens}.  She doesn't always do what I'd want her to, but I can live with that.''



``This sets a precedent,'' Miss Militia said.  ``One that I doubt our superiors would be happy with.  One I doubt the \emph{public} would be happy with.''



``When I showed up the night you guys outed me to the public, Tagg was boasting about your fantastic public relations department,'' I said.  ``How virtually anything could be sold to the public, given time.''



``It's ultimately up to the Director,'' Triumph said, ``But what if, hypothetically, we had a figurehead leader, with Miss Militia as the person that was really calling the shots?''



I shook my head.  ``Not good enough.''



``You actually have the temerity to play \emph{hardball}?'' Tagg asked, his voice rising a notch.  ``I think you're missing the fact that you're securely in our custody, and you \emph{already} surrendered.  If it comes down to it, we can see you shipped off with Dragon and Defiant, keep you airborne and away from any large body of insects until your trial by teleconference.''



``And my teammates?'' I asked.



``That's up to you,'' he said, ``But I don't think you have it in you to sacrifice them for\ldots \emph{this}.''



``I guess I have a higher estimation of them than you do.  Don't tell your people to stop underestimating \emph{me}, only to slip up and expect to win wholesale against the rest of the Undersiders.  I think they'd surprise you.  Surprise \emph{all} of you.''



``You said you need compromise,'' Miss Militia said.  ``But you won't budge on this point?  A figurehead leader would keep the public content and give you what you're asking for.''



``What I \emph{want},'' I said, ``Is to set a \emph{precedent}.  Fixing Brockton Bay doesn't do a thing, if we don't leave doors open to fix things elsewhere.  If one cape becomes head of the local PRT, then it could happen elsewhere.''



Director Tagg drummed his fingertips on the metal table for a few seconds.  When he spoke, his tone was derisive.  ``Your arrogance boggles the fucking mind.  You want to change the world, and you think a confession on television and the threat of your friends attacking the PRT will be incentive enough?  You're not that big a fish.''



``I don't want to change the world,'' I said.  ``I want to make it \emph{possible} for things to change.''



``Semantics.''



I sighed.  My glasses were slipping down my nose.  I had to bend over to put them in reach of my hand so I could push them up.



``Is that it?'' Miss Militia asked.



``One more thing,'' Mr. Calle said.  ``My client has a request.''



All eyes turned to me.  I straightened.  ``I recognize that I'm asking for some big things.  I'm hoping that the\ldots scale of some of what I'm asking for is tempered by the fact that this is all \emph{constructive}.  It puts us in a better place and leaves us prepared to face down the real threats: the impending apocalypse, the Endbringers, the forces who'd want to move into this city and abuse the portal.  I'm going to ask for one more thing in that vein.  Don't send me to the Birdcage.  Don't send me to juvie, or hang me for treason.  It's\ldots not constructive.''



``What would you have us do?'' Mrs. Yamada spoke up.



``\emph{Use} me.  I get that it wouldn't work, having me join the Wards.  Too much baggage.  But\ldots the end of the world hinges on Jack Slash doing something within the next two years.  You absolved Armsmaster of his crimes and sent him out to hunt them down.  Do the same with me.  I can cover a lot of ground in a search, I have experience fighting them, and if you needed it, nobody would even have to know I was doing it.  I'd be one more body on the ground, relatively discreet, and maybe that gives us all a slightly better chance of keeping Dinah's prediction from coming to pass.''



I wasn't even done talking when I saw the looks, felt a sinking in my gut as the various people in charge exchanged glances.  Tagg smiled a little.  Miss Militia looked\ldots concerned.  The only person who looked as confused as I felt was Clockblocker.



``What?'' I asked.



``Your intel is out of date,'' Tagg said.  His heavily lined eyes were staring at me, studying me.



``What?'' I asked.  ``You already stopped them?''



``No,'' he said, and the word was a growl.  He didn't elaborate further.



``Taylor,'' Miss Militia rescued me, ``Do you know where the Slaughterhouse Nine went after leaving Brockton Bay?''



``A series of small towns, then Boston,'' I said.



``Yes,'' she said.  ``And they struck one target after Boston.  Toybox.''



I remembered seeing the name on Tattletale's bulletin board.  ``Who or where is Toybox?''



``\emph{What's} Toybox, you mean,'' the Director said.



``What's Toybox?'' I asked.



``May I?'' Miss Militia asked Tagg.  He gave her a curt nod, and she took hold of the laptop in front of him.  It took her a few moments to log in and open the page.  She unplugged the cord from the laptop and handed it to Mrs. Yamada, who handed it to my lawyer.  He set it so we could both see it.  Mr. Calle clicked the touchpad to page through the various images and documents.



``Toybox is a black market organization,'' Miss Militia said.  ``Tinkers who operate solo find life rather difficult, due to a lack of resources and the fact that gangs and government organizations are very, \emph{very} persistent when it comes to recruiting them.  Faced with the prospect of spending their lives on the run, trying to avoid being forcibly recruited into one organization or another, most turn to the Protectorate or the Wards.  For those few who don't, Toybox is\ldots \emph{was} a refuge of sorts.  Tinkers would join, share technology, stay in the enclave as long as they needed to build up a reputation and whatever tools they needed, they would share thirty-three percent of any proceeds with the rest of the group, helping to keep others afloat.  Toybox sustained itself with barter, by moving frequently, operating between the scope of heroes and villains, and by selling less-than-legal goods to criminal groups.''



I could see the images, grainy black and white photos of various tinkers huddled together, or standing behind tables loaded down with ray guns and the like.  There was a chronology of sorts, to the point that I could see the group evolve, some leaving as others joined, the enclave shifting from a group as small as four members to as many as fifteen.



``The Slaughterhouse Nine attacked them at the end of June,'' Miss Militia said.  ``In doing so, they appropriated all of the tinker technology and all of the \emph{tinkers} that were staying with the group.  See page thirty-six and on.''



Mr. Calle paged forward until the images showed up.



Pyrotechnical.  A tinker focusing on flame manipulation, special effects, guns.



Cranial.  A tinker specializing in neurology.  Brain scans, draining thoughts, recording thoughts.



Big Rig.  A tinker who built drones that built things in turn, particularly buildings.



Bauble.  A girl who specialized in glassworking and glassworking tools, including tools that could turn inorganic matter into glass.



Dodge.  A boy, twelve, who made access devices for pocket dimensions.



Toy Soldier.  A powersuit user with a suit the size of a small building.



Glace.  A tinker specializing in cryogenics and stasis.



``The Nine have access to all of their work?''  I felt an inarticulate feeling of horror creep over me.  I couldn't imagine anything particular, but anything that enhanced the capabilities and options that Slaughterhouse Nine had at their disposal?



``And access to the work of Blasto, a \emph{cloning} specialist they assaulted and kidnapped in Boston,'' Miss Militia said.



I sat back and the chain of my cuffs went taut, my arms stretched out in front of me.  ``This doesn't change things.  If anything, you need all of the help you can get.  This is serious.''



``It's complicated,'' Miss Militia said.



``Seems pretty damn simple,'' I said.



``No,'' she said, shaking her head.  ``Because they're \emph{gone}.  They stopped.''



I shut my mouth, staring.



``The Slaughterhouse Nine attacked Toybox, taking the group's devices for themselves, and they disappeared.  We suspect they used Dodge's devices to exit into a pocket dimension, and by the time we'd found a way to follow, they'd exited elsewhere.''



``They're dimension hopping?''



``Dodge's devices only exit from Bet to pocket worlds he creates with his devices, back to Bet.  We believe they exited somewhere on Bet, possibly in another state, then used \emph{another} device to hide.  Which would be where they are now.  Without knowing where they entered that particular pocket, we can't hope to find them,'' Miss Militia said.  ``We know their patterns.  They tend to cut a swathe of destruction across North America, and it's rare for even a handful of days to pass without them taking any action at all.  Between the PRT's past experience with the group, our thinkers, and the fact that they haven't made an appearance in nearly ten days, we believe we've worked out what they're doing.''



I stared at the laptop.  It was still on the last page.  Glace.



``Cryogenics,'' I said.



``Stasis,'' Miss Militia agreed.  ``The pressure grew too intense, with Defiant and Dragon's pursuit, they weren't recovering from losses fast enough.  They've gone into hiding, and we think they plan to \emph{wait}.''



\emph{Wait}, I thought.



``How long?'' Clockblocker asked.



``We can't know for sure,''  Miss Militia replied.  ``But if they've put themselves in a cryogenic sleep, they could wake and resume their normal activities days, weeks, months or \emph{years} from now.  Depending on the resources they have available, they might well emerge with clones of their current members at their side.''



\emph{Tattletale should have told me}, I thought, even as I knew why she hadn't.  Her power had been out of commission.  \emph{She'd} been out of commission.  We'd known the Nine attacked the Toybox, but we'd missed what that meant in the grand scheme of things.  Through a combination of Tattletale's ailment and a hundred other small distractions, we'd missed out on the reason Defiant and Dragon had been able to abandon their hunt for the Nine and visit Arcadia.



``Does Jack know?'' I asked.  ``I mean, I know he knows he's supposed to end the world, but does he know he sets it in motion within two years?''



Miss Militia shook her head.  ``We don't think so.  Which means that, unless there's something specific they want to wake up for, we can't even begin to guess when he'll have his team wake up.''



Silence hung in the air for long seconds.



``Now you know.  These are your demands?''  Tagg spoke up.



``We'll need to discuss things and revise our terms with this new information in mind,'' Mr. Calle said, glancing at me.  I nodded once.



``Better do some \emph{heavy} revision,'' Director Tagg said.  ``And do it fast, because it's not that long until sundown, and I won't be accepting any of your terms as they stand.  You said it yourself, nobody wants this fight.''



I frowned, watching each of them making their way out of the interrogation room.



Tagg joined Miss Militia's side, and I couldn't help but notice the way she adopted a guarded position, folding her arms as he approached.  It gave me a flicker of hope.



Until the bugs I'd planted inside the fold of Tagg's collar caught a fragment of something he was saying.



``\ldotsher father.''





