





The door slammed shut as the last of the heroes departed.  They joined the PRT uniforms and Wards who had gathered just in front of the elevator, leaving me and my lawyer to talk in private.



It should have been quieter, but things got \emph{more} disruptive.  The moment the door was shut, a handful of seconds passed, and then \emph{everyone} started talking.  Mr. Calle saying something to me, Director Tagg talking to his deputy and Miss Militia, Clockblocker talking with his teammates.



``This is more or less what we expected\ldots'' Mr. Calle was saying.



``Call him.  And let me know when he arrives.'' Director Tagg, talking about my dad.



``She wanted to defect,'' Clockblocker told the waiting Wards.  ``Join Defiant and Dragon, go hunt the Slaughterhouse Nine\ldots''



``You created pressure with the deadline, he's trying to turn it around on you\ldots'' Mr. Calle said.



``I \emph{know} he's trying to turn it around on me,'' I said.  I slid forward until I was sitting on the very edge of the chair, my elbows on the table, forehead resting against my hands.  ``I didn't think he'd be this stupid, and I kind of hoped someone would speak up, give a little momentum to what I was proposing.''



``People are stupid,'' Mr. Calle said.  ``The question is how we can \emph{use} that.  If we--''



Some heroes simultaneously began to voice \emph{their} thoughts, to the point that I failed to take \emph{any} of it in.  It was too much.  Too much input, all together.  I couldn't track it all.  I shut my eyes.  ``Do me a favor?''



``You're the client.''



``Five minutes,'' I said.  ``Five minutes to think, with some quiet.''



``Would pen scratches bother you?''



I shook my head.



Mr. Calle didn't reply to that.  Instead, he started writing on a pad of yellow, lined paper, apparently unconcerned that I'd just brushed him off.



``\ldots{}a hot button for her,'' Mrs. Yamada was telling the Director.  ``It's a pattern, with the timeline we established.  Something happens to her father, and she escalates.''



``Yes,'' the Director replied.  ``But let's not talk about that here.  Not while she could be listening.  We give Kid Win's drones a chance to check us over before talking about any of that\ldots''



``Hunting the Slaughterhouse Nine?'' Vista was asking.  The Wards were lagging a short distance behind the adult members of the PRT and Protectorate.



``Yeah.  As in, step down from her position here, stop the guys who are supposed to end the world,'' Clockblocker said.



``She didn't kill any, did she?'' Kid Win asked.



``Grue supposedly killed Burnscar, Piggot killed Crawler and Mannequin, they killed Cherish themselves, basically, Vista finished off Shatterbird after things caved in on them at the Echidna fight\ldots no, Skitter didn't kill any, I don't think.  She was there, though.  Have to give her credit, she made a difference in that last fight with Mannequin and Crawler.''



``Which doesn't matter,'' Tagg said.  He'd overheard, it seemed, and stopped at the open elevator door.  ``Because she also wanted us to condone criminal activity in this city.  Think about what that \emph{really} means.  Your careers would be dead in the water once people caught on to the fact that you weren't going after the \emph{real }threats.  You'd be known for being corrupt.  Flechette's actions threaten to taint this organization for some time to come..''



``Wait, wait,'' Kid Win said, ``Flechette?''



``We're telling them?'' Clockblocker asked.  ``It's confirmed?  It's not a trick?''



``It's not Regent,'' Miss Militia said.  ``The timing doesn't fit.  No, it doesn't look like it's a trick.  She sent us an email and the details include only things she knows.  It \emph{feels} right.''



There was a pause.



``What happened?'' Crucible asked.



``Flechette is stepping down from the Wards program.  She is going to be assisting the Undersiders in the future, helping Parian,'' Miss Militia said.



``No!''  Vista said, raising her voice.  ``No!  She became a villain?  What\ldots what the \emph{hell!?}''



``Vista,'' Clockblocker said.  ``She was in love.''



``She was still one of \emph{us}.  Did you do something?''



I wasn't sure who she was talking to, until Tagg responded, ``No.  We didn't do a thing to her.  Everyone that's been in Brockton Bay over the past weeks and months has dealt with a lot, and I think this is her wrestling with something on her own.  I have immense respect for Flechette, and all I can do, all \emph{we} can do, is hope she comes to her senses.''



``What about her parents?  Her family?''  Vista asked.



``I can't talk about anything my patients discuss with me in my office,'' Mrs. Yamada replied.  ``I'm sorry.''



``She came from a broken home,'' Miss Militia supplied the information instead.  ``She bounced between her mother, her father and the surrogate mother who had attempted to renege on the deal they'd made and keep her.  With the number of times she changed between them and moved, I can't imagine she has strong ties to the idea of `home'.  Even within the Wards\ldots New York has five small teams, and she moved between them as she changed residences.''



``She didn't say anything about that.''



``It didn't matter in the here and now.  Her focus, her path, was school, her career with the Wards.  She didn't have much in the way of roots, but she had direction.  I think that the events following the Echidna crisis left her more devastated than she let on.''



``Can I call her?'' Vista asked.



``I don't know if that would be wise,'' Miss Militia said.



``Do,'' Tagg said.  ``Remind her what she's leaving behind, tell her how you feel, then let her be.  Too much pressure and she's liable to be stubborn.  Give her time to think, and you may sway her.''



``Okay,'' Vista said.



``When you're done, join the others in discussing battle plans.  I'd rather not wait for Skitter's forces to strike.  If it comes down to it, we mobilize first.''



``We'll be fighting Flechette,'' Vista said.



Tagg nodded.  ``Very possible.  If you don't feel confident you can do it in good conscience, then I won't make you.  In the meantime, I'm requisitioning capes from nearby areas.  If it comes down to it, I want to be ready for a fight.''



``And if they don't give us the chance?'' Miss Militia asked.



I missed Tagg's response.  It was monosyllabic.



``If the Undersiders try to avoid direct engagement and attempt to come at us from another angle?  Media?  Revealing telling details?  \emph{Financially?  }Through our families?''



``Oh shit,'' Clockblocker said.



``They wouldn't, would they?'' Crucible asked.



``They would,'' Kid Win said.  ``Probably.''



``They would,'' Director Tagg agreed.  ``And I already have ideas in mind.  This situation is \emph{far} from unmanageable.  Rest assured.  I'll need to make some calls.  Miss Militia, are you up for another walk?''



``Yes.''



Tagg stepped into the elevator, holding the door open.  It was too small for \emph{everyone} to fit inside, but Miss Militia, the deputy and Clockblocker joined him.



Mrs. Yamada started to step inside, then paused while standing in the doorway.  ``I'll be in my office all day.  If any of you need to talk about Flechette, or anything else that's going on, come see me.''



There was no reply.  There might have been nods, but I didn't have bugs on top of any of the Ward's heads.



The doors shut, and a few seconds passed, Kid Win, Crucible and Vista standing in the hallway with a handful of PRT officers.



``Fuck,'' Vista said.  ``Fuck this.  Fuck \emph{you}, Skitter, if you can hear me.''



I waited to see if there was more, but neither she nor her teammates said anything.  The drones Kid Win had made were doing a number on my bugs, catching me by surprise when they opened fire with lasers, striking from the other side of the room.  It wasn't easy to avoid them completely, when an exposed bug could get zapped, but keeping my bugs in hiding prevented me from seeing the drones themselves.



Miss Militia left the building, walking.  She wasn't quite out of my range when she made her first call.



``Mr. Hebert?''



I sighed, then shifted position.



``Everything alright?'' Mr. Calle asked me.  ``Needed to get centered?''



``Was listening in,'' I said.



``Listening in?''



``I can hear what my insects hear.  Tagg is confident.  He's calling in more capes, and preparing for a fight.  He's apparently not too worried about the Undersiders pulling something that \emph{isn't} a direct attack, but I don't know what he's got in mind, as far as trump cards go.  Miss Militia is apparently calling my dad, so Tagg can talk with him.''



``Wonderful,'' Mr. Calle said.  ``Anything else?''



``The Wards are upset over Flechette defecting.''



``Okay.  Something to keep in mind.  Now, this is difficult to say, but--''



Mr. Calle paused very deliberately.



``What?''



``I would never recommend my clients do anything illegal,'' he said.



``But you maybe suspect that if I had any leverage, I should exercise it?''



``I would never say any such thing,'' Mr. Calle said.  He smiled.  ``But now that you mention it\ldots''



``There are options,'' I said.  I thought about the areas of attack that Miss Militia had outlined.  Family would cross a line.  Something to shake their confidence in the coming conflict.  ``Can you pass on a message?''



``That would be a mistake, I think.  I walk a fine line as it is, and I won't have a hand in anything direct.''



I frowned.



``Let's talk about what I \emph{can} do.  First off, I think we should change things up.  As it stands, the Protectorate East-North-East holds Brockton Bay in a specialized state of emergency.  It's a legal wild west, with very little precedent holding things together.  Director Tagg reports to his superiors, who report to the United States government.  This circumvents a great many of the usual checks and balances.  Checks and balances I think we should put back into play.''



``How?''



``Contacting the District Attorney and bringing her to the discussion would tie Tagg's hands, but it would also tie yours.  We'd be working entirely within the law, certain items would be taken off the table.  You couldn't ask for condoned villainy, for example.  Charges would inevitably move forward against you, but these same things would tie him up in managing things.''



``Doesn't seem worth it.''



``It depends.  It's\ldots pressure.  The Director is focused on a half-dozen things at once.  There's a lot to be said for putting one more thing on his plate.  I know he's not trained in the particulars of law.  He'd be forced out of his depth, made to consult others, made to wrap his head around terms he's not familiar with.  It would mandate that you, as a minor, would need a guardian present.  Failing that, there's a great many hoops they'd have to jump through.  He's a soldier.  So long as this is a battlefield of some sort, he has a leg up.  We can make it something else.''



``Okay,'' I said.  ``We'd be adding pressure, turning things around so he's the one on his heels, but I'm still not convinced it's worth the price of admission.  Other options?''



``Media.''



``He doesn't care about image,'' I said.  ``He said he figures it'll get patched up with good PR in a matter of time, a few days back.''



``It won't hurt him as badly, then, but he's more likely to make a mistake if it's not something he pays attention to.''



``An option,'' I said.  ``It sets a bad tone, though.  I'm really looking for \emph{cooperation}.  I'm putting everything on the line in the hopes of getting it.  I don't want them to be enemies, not any more than they are.  And I don't know that just talking to the media is going to be enough to get the results I want.''



``It isn't, frankly.  Are there points you're willing to compromise on?''



``It doesn't matter,'' I said.  ``Because he's not willing to meet me halfway.''



Mr. Calle rubbed his chin.  ``Okay.''



``So we need leverage, and it can't be legal.  Going to the District Attorney or the media has drawbacks.''



``Yes.''



``Then I need you to get in contact with Tattletale.  Only we'll be above-board, mostly, about how we handle it.  She's been arranging things for a while.  Now it's time to figure out just how much clout she has.  We'll hit them with the biggest card we have.  We'll make a play for ownership of the portal.  Successful or not, it'll distract them.''



``I'll do what I can to get in touch with her, then.  My firm's assets will be at your disposal, of course.''



I nodded.



He stood from his seat to make the call.  Apparently he didn't find them much more comfortable than I did.  He paced as he waited for the phone to ring.  ``Cecily?  Need you to pull some strings.  And route me to someone, best if it's untraceable.''



It wouldn't be a direct call.  That didn't make sense.  I focused my attention elsewhere in the building.  The outlet that fed Kid Win's anti-bug drones\ldots I found the wiring in the walls and ordered cockroaches to start chewing through it.



Petty, maybe, but I didn't want to be disarmed, not with the way things were going.



The heroes were returning, Sere and Dovetail entering the lobby.  I planted bugs on Dovetail as she made her way indoors, and as discreetly as I was able, I transferred the bugs to Tagg and Miss Militia, who were waiting.



``They're moving,'' Dovetail said, ``\ldots soldiers.  Arming civilians.  Squads no larger than five people, across the city.''



``Good,'' Tagg said.



``That's all.''



``Tell the others,'' Miss Militia said, ``Adamant's getting a cycle retooled to handle more weight before he leaves again.  He'll go with Triumph.  Log it all in the system.''



``Will do,'' Dovetail said.  Miss Militia patted her on the shoulder as she made her way inside.



Miss Militia and Tagg remained in the lobby, by the hallway to the elevators.  They didn't say much.  A few words on degrees of lethal force, but no camaraderie, not even much in the way of small talk.



My cockroaches found their way through the wire, and promptly died as they came in contact with the live circuit.  A breaker blew, but Kid Win didn't seem to react.



Hopefully the drones wouldn't get a chance to recharge.



A few minutes passed, as my lawyer got in touch with someone, and started talking about media contacts.  Then my father arrived.



I could sense him as he got out of a truck in the parking lot, making his way inside.



``Mr. Hebert,'' Miss Militia said, extending a hand.



My dad shook it.



``Thank you for coming in again,'' Director Tagg said.  He extended a hand.  Again, my father shook it.



``My office?'' Tagg asked.



My dad nodded.



My pulse was pounding as Miss Militia, Tagg and my father entered the elevator and made their way upstairs.



``She's here?'' my dad asked.



``In a room downstairs with her lawyer,'' Miss Militia answered.



``She hired him herself?''



``I imagine she did,'' Miss Militia said.  ``With the speed he pulled things together, I suspect she may have more working in the background.  Crime does pay, if she's paying their salaries.  They're apparently top of the line, as parahuman defense attorneys go.''



``I can't believe this is all real.''



``It is,'' Miss Militia said.  ``It's very real.''



``And very real blood will be shed tonight,'' Tagg said, ``If we can't rein her in.''



\emph{Rein me in.}



They exited the elevator and made their way to Tagg's office.



``These,'' Tagg leaned forward, and my bugs could hear something move.  ``Are the charges as they stand.''



I didn't sense it, but my bugs could hear papers rustle.  I might not have identified the sound if I hadn't had the context.



A few long seconds passed, and I could hear the rustling again.  The turning of a page.



I clenched my fist.



``Problem?''  Mr. Calle asked, covering the mouthpiece of his phone.



``My dad's here.  They've got him in Tagg's office, and they're filling him in on \emph{their} version of events.''



``Right.  Let's put a stop to that.  I'll be back.''



Phone still pressed to his ear, he picked up his briefcase, tapping on the door three times with the side of his shoe.



A PRT uniform unlocked and opened the door, and my lawyer strode out.  It shut behind him.



Upstairs, my dad turned another page.



He was reading through it all.  All the details I'd gone over with my lawyer, only without my feedback, without my voice to point out the places where they were going a little overboard, naming charges they could throw at me, without checking whether they could stick.  Not that the difference was that big, comparing what I'd actually done to what they were accusing me of.



I heard the sound of him flipping through the last few pages before he dropped the pad on the table.  ``Okay.''



``She's in a lot of trouble,'' Tagg said.



``This isn't news to me,'' my dad answered, his voice quiet.



``If the charges went through, she would face being charged as an adult.  The three strikes protection act wouldn't mitigate things.  I'd say the worst case scenario is execution, or indefinite detention in the Birdcage, but the best case scenario for her isn't much better.''



My dad didn't reply to that.



``Her power means we can't keep her in a conventional prison.  She's too flexible, too versatile for us to use any of our current means of keeping her from using her ability.  Even today, contained in a cell, she's been literally `bugging' us to track our movements and listen in on conversations.  We had our tinker put together a countermeasure, but it's not perfect.''



Again, my dad was silent.



``I have two daughters.  Four and six years older than Taylor,'' the Director said.  ``I can't imagine.''



``I can't either,'' my dad said.  ``Like I said, it doesn't feel real.''



``I'd like you to come with me the next time I speak to your daughter.''



``She didn't listen to me before, she won't listen now,'' my dad said.



``I didn't ask you to come because I thought you could convince her,'' Tagg said.  ``You don't have to say anything, as a matter of fact.''



\emph{What was he up to?}



My lawyer had reached the top floor, and was striding between cubicles and desks.  He raised his voice to ask a question I couldn't make out, and someone answered him.  He altered his course slightly in response, walked with more purpose, directly for Tagg, Miss Militia and my father.



``I'd like to talk to her alone,'' my dad said.



``We can arrange that,'' Tagg said.



I clenched my fists.  Using my dad as a \emph{pawn}?  Damn right I was going to escalate.  Which, I suspected, was exactly what Tagg was aiming to achieve.  This was something to put me off balance, just like we were looking to do to him by way of leveraging control of the portal.



My lawyer knocked on the door and then opened it without waiting for a response.  ``My client would like a word.''



``Of course,'' Tagg said.  As the four of them exited his office and made their way to the elevator, I turned the two words around in my head.  Had he sounded sarcastic?  Did he simply \emph{expect} me to interrupt?



I couldn't say.  I could only wait as they made their way downstairs.  I was stuck, my back hurting where my arms were in a more or less fixed position.  I stood, stretched as well as I was able, tossed my head to one side in an attempt to get my hair out of my face.  When that didn't work, I bent over and lowered my face to my hands to tidy my hair.



Then I sat, stewing in unidentifiable emotions.  Trepidation, dread, fear, guilt, shame, anger, relief\ldots none I could put a finger on.



``Did you know?'' Miss Militia asked.



``Me?'' my dad asked, by way of response.



``Who she was?  What she was?''



``Yes,'' he said.  I could feel alarm sing through me, inexplicable, but jarring.  Then he seemed to change his mind, ``No.''



And the emotion that hit me at that was just as strong as that misplaced sense of alarm.



Damn Tagg.  Damn him for bringing my dad into this.



The four of them stopped outside of the cell.  Miss Militia used her phone to unlock it, and Tagg gestured for my dad to enter.



I saw him hesitate as he stepped into the room, dark sheet metal, a reflective pane of one-way glass, the metal table bolted to the floor, my handcuffs, locked to the table in turn.  Me, with my hair in some disarray, a touch damp from the shower and ineffectual toweling, from sweat, in my black uniform with the word `villain' marked clearly across it.



I could see it, his expression changing, the disbelief he'd professed to becoming something else entirely.



His feelings were as mixed as mine.  I could tell just by looking at him, by imagining what he'd been through, the person standing by, dealing with the aftermath of everything I'd done.  His frustration, his confusion, pain, and embarrassment.  His loneliness, disappointment, his fear.



And, somehow, as though it were too much to bottle in, it seemed to boil over in the form of one singular emotion.  I could see his jaw shift as he clenched his teeth, met my eyes and looked away.  The sudden agitation that seemed to grip him, as he opened and closed his fists.



Tagg and Miss Militia had reached the interior of the room on the other side of the one way mirror, while Mr. Calle stood in the hallway, speaking on the phone.  I stood from the chair as my dad approached, his body language making it all too clear what he was about to do.  Miss Militia took one look and reacted, turning around to hurry back out of the room, to intervene.  Tagg said something, two words I couldn't be bothered to decipher, and she stopped in her tracks.



My dad raised his hand, palm open, and I closed my eyes, lifting my chin to take the hit.



It didn't come.  My dad wrapped his arms around my shoulders instead.  I squeaked, and I couldn't say whether it was because he was squeezing me too tight or if it was because of an overflow of emotion similar to the one he'd just displayed.  I stood there, unable to return the hug with the way I was cuffed to the table, unable to speak around the lump in my throat.



When minutes passed and we hadn't exchanged a single word, Tagg and Miss Militia stepped out of the observation room, signaling Mr. Calle.



``Let's talk,'' Tagg said.



I broke away from my dad.  Blinked where there were tears in the corners of my eyes.  I didn't care if Tagg saw.



``I'm waiting on a response from my colleagues,'' Mr. Calle said.  ``There's no reason to speak further, unless you're capitulating.''



``No,'' Tagg answered.  ``But I'd like to go over the main points.''



\emph{This was why he wanted my dad here}, I thought.



``You've informed me that your teammates, many of whom are known \emph{murderers}, are going to declare war against the PRT in three hours and twenty minutes, without word from you.''



My dad took a seat to my left, watching me carefully.



``Yes,'' I said.



``You've described them as unpredictable.  They're undeniably dangerous.  You think they'll hurt people.  They'll pull out all the stops, to get you back, and to hurt \emph{us}.  The good guys.''



``Yes,'' I said, not taking my eyes off Tagg.  ``But I don't think you're a good guy, Director.''



``I don't think you're a good person either,'' Tagg said, ``and the court of public opinion is likely to agree with me before they agree with you.''



``Let's not resort to name calling \emph{this} early in the discussion,'' Mr. Calle said.



``Right,'' Tagg said, ``It wastes time, and you have very little.''



``Neither of us want this to happen, Director,'' I said.  ``Neither of us have time, and neither of us want a war.  Except maybe you do.  Maybe you think you'd win, and it'd be a bump in the PRT's ratings.''



``No,'' he said, ``I think, like any altercation, both sides would lose something.  But let's talk about your terms.  You want amnesty for your criminal friends?'



I was acutely aware of my dad watching me.



``Yes,'' I said.



``You want to depose me, raising Miss Militia to my place, and in the doing, force the PRT to relinquish all ideas of humans governing \emph{para}humans, to help keep those with incredible power in check.''



``Yes.''



``And you wanted me to allow you to become an official vigilante, leaving your group behind while you worked to hunt down psychopaths with powers.  I've explained why that can't happen.  I'm not sure if you intend to change your demands, or--''



``I'll go to the Birdcage if I have to,'' I said.  ``Because the rest of it, I believe in it enough to make the sacrifice.''



``Taylor,'' my dad said.  The first words he'd said to me since the breakfast we'd had together, on the day I'd been outed.  ``Why?''



``Because we're \emph{losing}.  We're so focused on the little things, on petty squabbles and factions and vendettas, that we're losing against the \emph{real} dangers.  The Class S threats.  The fact that the world's going to end in a year and eleven months.  Did you hear about that?''



He shook his head.  ``I\ldots I read the letter you left me, at Annette's grave.  Realized it was probably what you were trying to write, the night you left.  Before you changed your mind.''



The night I left, so long ago.  When I'd first met Coil.



``A lot of what I did, it was to stop the man who \emph{really} wanted to take over the city.  Who would have been far worse than any of us Undersiders.  And I did \emph{that} because he had a little girl captive.  Dinah Alcott.  She could see the future, and she says the world ends in two years.''



My dad shook his head, ``No.''



``Yes.  The heroes know it.  It's a big part of why the PRT is falling apart.  You've heard about that on the news?''



``I\ldots some.  But I haven't paid much attention since I found out that you--''



``That I'm a supervillain,'' I said.



He flinched visibly at that.



``Interesting,'' Tagg cut in.  ``That you call yourself that.  You say you've had justifications for what you've done, but you call yourself a villain.''



I wanted to hit him, for cutting into my conversation with my dad, for polluting my attempts to explain things.



``I am,'' I told him.  ``I've done bad things.''



``Left a trail of devastation in your wake.''



``Yes,'' I said.  ``And I'm willing to pay the price.  I'll go to the Birdcage, a place you described as a literal hell on Earth.  A place where people just as scary as the ones I've spent the last few months fighting stay.  A place where some of \emph{those very people} are currently imprisoned.  Lung, Bakuda, Trickster.  They probably want to inflict fates worse than death on me.  But I'll do it.  Because I really truly believe the world needs the PRT, or \emph{a} PRT, one without lunatics like you in charge, and maybe bringing me in helps keep a handful more capes in the roster, keeps my friends secure where they are, so they can \emph{help}.''



I was heated, my words angry.



``Your friends,'' he said.



``My friends.''



``That's the rapist, Jean-paul?  Alec?  A murderer.''



``Regent.  He was the son of a supervillain, screwed from the get go, and yeah, maybe some shady stuff went down, way back then.  I think he's\ldots not in love, but he's close to Imp.  Somewhere between love and friendship, maybe.''



``Imp.  She's the one who makes it a game, to psychologically and mentally torture gang members who step foot in her territory, until they have mental break downs.''



``Yes,'' I said, through grit teeth.  ``It's more complicated than that, she's been through a lot, but yes.  And I heard directly from people who were grateful to her for scaring off the \emph{real} rapists and murderers.''



He didn't pay me any mind.  ``Who else is there?  Hellhound.''



``She prefers Bitch,'' I said.  ``But she's Rachel to me.''



``Who had her monster dogs chew up innocents who'd gotten in her way.''



``It was a bad time for her.  Weren't you just excusing Flechette, because we've all been through some shit?  I know Rachel as the person who takes care of wayward souls, grown men and children who are lost in a way even \emph{we} can't fathom, with the things we've been through.''



``And Grue?  Do tell me how you see him.''



``I liked him,'' I said.  ``If I'd stayed with them, maybe he and I would have tried to make it work.''



``Romance.''



I met my dad's eyes.  His forehead was creased with worry.  My power was buzzing around the periphery of my consciousness.



I found refuge in the bugs, paid attention to their movements as they avoided the remaining drones, found my center, so to speak.  \emph{Calm.  He wants me upset}.



``Romance,'' I said.  ``He was my rock, when I needed a rock.  And I was his, when--''



``When he snapped,'' Tagg cut in.



``It wasn't like that.''



``He was the stable one, until he wasn't stable,'' Tagg said.  ``Until he killed Burnscar.  Yet I suspect he's the one in charge, now that you've left?''



``Yes,'' I said.  ``And with the dozens, \emph{hundreds} of people I've tried to take care of or whose lives I've saved, I trust Grue to look after them and keep the peace.  I wouldn't give him that responsibility, with all the time and effort I've invested in them, if I didn't trust him.''



``Very generous,'' Tagg told me.  ``And Tattletale.  Where do I even start?''



``With the fact that she was my best friend.  That she's maybe our best bet at \emph{understanding} what's going on?  Understanding the Endbringers and what they're doing?  Understanding \emph{powers}?  Finding the Nine before they bring about the end of the world?  Understanding \emph{how} the world ends?''



``All of this, from the girl who used her power to convince her brother to kill himself, before fleeing, spending years on the streets, stealing wallets and using the account numbers to take whole \emph{fortunes}?''



``All wrong,'' I said.



``And who planted the seeds that led to Panacea breaking down and mutilating her sister.''



``Those seeds were planted a long time before we talked to Panacea,'' I said.



This was what Tagg had wanted.  He'd devastated my defenses, bringing my dad into this.



``Nonetheless,'' Tagg said, leaning back.  ``So, Danny Hebert, what do you think about your daughter's friends?''



My dad glanced at me, then looked at the Director.  ``I know less about them than either of you.''



``That's not important,'' the Director said.  ``I just want you to answer one question for me.  Assume we're \emph{both} right.  Me and your daughter.  Assume that they're everything we described them as.  Do you \emph{really} want them in control of this city's underworld?''



Again, my dad looked at me.



``No need to double-check with your daughter.  I'm wanting your honest opinion, as a man on the streets, from someone who has to live in this city without any real say over what happens in the cape-on-cape fights and politics.  Do you really want them in charge?''



``No,'' my dad said.



I did my best not to show it, but the word was like a punch in the gut.



``I'm sorry, Taylor, but--''



``Are they really that much worse than the ABB?  Than Empire Eighty-Eight?''



``With them, we\ldots'' my dad trailed off.



``With them, we could \emph{pretend }things weren't bad!'' I said, ``But they were worse.  You \emph{know} they were worse.  The people you worked with, the addicts, the people without money\ldots''



``Does it matter?'' Tagg asked.  ``You don't have your dad's support, what makes you think you'd get anyone else's?''



I grit my teeth.



``No,'' my father said.



``Hm?''  Tagg raised his bushy eyebrows.



``No.  I think you're wrong there,'' my dad told Tagg.  ``She has support.  When you attacked her in the school, there were people who stood by her.  If I'm being honest, I don't get it, I don't want those people in charge, but I don't want \emph{any} villains in charge.  I don't understand the politics behind this, or the context, but I trust my daughter.''



``Of course you trust your daughter.  The curse of being a parent, I know it well.''



``You wanted my opinion,'' my dad said, his voice a little firmer, ``You get my opinion.  \emph{Others} believe in her.  I trust her, even if I don't know enough to follow what this is all about. Even if I barely feel like I know her right now, I can look her in the eye and know that's the same girl I've spent the last sixteen years with.  With some of the worst qualities of my wife and I, and a lot more of the better ones.''



``I wonder how long that opinion will hold,'' Tagg said.  ``Because we have, what is it?  Three hours and a handful of minutes?  Then the war \emph{she} set in motion hits this city.''



``It can be avoided,'' I said.



``If we cave in to your extortion,'' Tagg said.  ``Except you think too small, \emph{Skitter}.  It's a common flaw among teenagers, however powerful they are.  They attend high school, and all they can see is the school, their peers.  Tunnel vision.  You're the same.  You're focused on this city, but you don't see what happens elsewhere.  You don't see the \emph{ramifications}.''



``Which are?''



``You'd be strengthening the PRT a little in the short-term, but the long-term?  Letting villains take charge, taking the humans out of the PRT, condoning villainy?  It would doom us all.  What you're threatening us with?  It's only one fight.  And maybe it's ugly, but it's one fight.  If they kill us, if they become monsters of the Slaughterhouse Nine's caliber to defeat us, then \emph{we} win.  Your side wins the battle, loses the war.  If you don't go that far?  If you leave us in a state to recover?  We pick ourselves up and we lick our wounds, and then we rebuild.''



Tagg cupped his hands, moving them as if balancing a scale.  ``One fight, one set of casualties in one area of one medium-sized city, compared to consequences that reach across North America?  Across the world?  It doesn't measure up.''



I glanced at my lawyer.



``You don't have an answer for me?'' Tagg asked.



``I have one,'' I said.  \emph{I hope}.



Mr. Calle looked at his phone, then gave me one curt nod.



``What?'' Tagg asked.



``It's in the news,'' Mr. Calle said.



Tagg and Miss Militia simultaneously reached for their smartphones.  I was probably as tense as they were, as they thumbed past the security screens and found news sites.  Miss Militia was a few seconds faster than Tagg.



``What did you do?'' she asked.



``It's all legitimate,'' I said.  ``I'm pretty sure.  Legal enough.''



``What is it?'' my dad asked.



``Property,'' I said.  ``I expect a great amount of property just changed hands.''



``Who's Sierra Kiley?'' Miss Militia asked.



It was all I could do to keep from smiling with joy.  Of all the people to serve as a public face, Tattletale had found Sierra.  Someone I \emph{owed}, in many ways.  Someone who'd, maybe, followed recent events and rethought her initial doubts.



``No idea,'' I said, maintaining my poker face.



``I don't understand,'' my dad said.



``Quite simple,'' Mr. Calle told him.  ``I believe the PRT has become aware that properties in a \emph{wide} area around the portal in downtown Brockton Bay, previously under the control of various individuals and groups, just exchanged hands, finding itself in the hands of one singular individual.''



``And that one individual is in thrall to the villains who control this town,'' Tagg said.



``I resent the notion,'' I told him, and I allowed myself a small smile.  ``But it would be amusing, if it \emph{were} true.  You might even have to rethink what you were saying about how narrow my worldview is.  I mean, that's a whole \emph{other} world.  Anything \emph{but} narrow, when you think about it.''



``You're not as clever as you think you are,'' he said.



``Probably not,'' I said.



``You're playing out your hand.''



``And you're bringing my \emph{family} into this.  Remember how our little feud started?  \emph{You} crossed the line.  You made the call to out me, because you wanted me in custody.  Congratulations, you got me in custody.  You broke the unwritten rules, because you think that you don't have to obey them, since you aren't a cape.  Except you're forgetting why they exist in the first place.  The rules keep the game afloat.  They keep \emph{everything} afloat, at the core of it.  We all know the PRT is a sinking ship.  You don't agree with what I'm doing?  Fine.  But at least I'm trying to keep it afloat.''



``And you?'' my dad asked.  It took me a second to realize he was looking at Miss Militia.



``What about me?'' she asked.



``You've been quiet.  Are you here just in case my daughter turns violent?''



``No.  She's not violent.  Not in that sense.''



``You don't have anything to say?''



``As grateful as I am for the right to free speech,'' Miss Militia said, ``I'm grateful for the right to \emph{silence} as well.''



``Then you don't agree with your Director?''



``I didn't say that.  What I'm saying is that there's no right answer here, and I'm glad I don't have to be the one to make the decision.''



``Isn't that cowardly?''  I asked.



``No.  It's human, to not want to make the hard choices,'' she said.  She raised one boot off the ground and placed it on the corner of her chair.  ``And it's good strategy to conserve your strength.''



``We're not fighting,'' I said.  ``We're not going to get tired.''



``Physically?'' she asked.  ``No.  Emotionally?  Mentally? Yes.''



``You're anticipating the fight,'' I said.  ``You don't think there'll be a consensus in time.''



She shook her head, then used one hand to fix her hair, tucking it behind one ear.  ``No.  I don't think there will be a fight.  I hope there'll be a consensus, but it's not necessary.  Your ploys with the portal, controlling the territory around it, it's clever, it'll take a lot of time before we can pass legislation or conduct a thorough enough investigation to justifiably seize it.  But I'm not worried about that, either, nor am I concerned about the damage Tattletale could do in other areas.''



``Then why do you need to conserve your strength?'' I asked.



``Because we're dealing with the devil,'' Miss Militia said.  ``I'm angry at you, Taylor, and half of that is because you put us in this situation, a set of circumstances where we're liable to lose either way.  Because I agree with the conclusions you came to, how the PRT is needed, the need for compromise, and because I can't condone how you \emph{approached} those conclusions.''



She shifted position, and the black-green energy of her flickered from her right hip to her right hand, appearing in her hand, amorphous and shapeless, as if searching for a form to take.  When she didn't grasp it, it darted to her left hip, and the metal of a cutlass clinked against her seat.



``But I really hate you because we had to call \emph{her,}'' Miss Militia intoned.



\emph{Her}?



Tagg looked at his phone.  ``Assuming she's on time, it'll be less than ten minutes.''



``Her?'' my dad asked.



``You've played your part,'' Tagg responded.  ``Go.  It'd be better in the long run.  Wash your hands of this, leave.  Your daughter's in custody, she's going to one prison or another.  You can go home and know that it was inevitable, and that this was the best outcome.  It takes a few years maybe, but you lament your mistakes, and you eventually make an uneasy peace with what happened to your daughter.''



``And if I stay?''



``You won't have any of that peace of mind,'' Tagg said, and that was all.



My dad looked at me, ``I think you're wrong.  Everything before this, it was the times where I thought I had to walk away, \emph{look} away, times where I thought things were inevitable, that I regretted the most.''



He took my hand.  ``I'll stay.''



``Thank you,'' I murmured the words.



Our guest didn't arrive right away.  It might have been fitting, in a dramatic way, for her to appear as we finished our dialogue, but things weren't so carefully orchestrated in the real world.



``Those things they said you did?'' my dad murmured.



``Mostly true,'' I said.



He squeezed my hand for a moment, but it wasn't \emph{reassuring}.  Something else.  Concern, maybe, channeled through a simple gesture.  Concern for me, for what I'd become.



I wanted nothing more than for my dad and I to talk for a month \emph{straight}, just to hash things out, to form some kind of balance, some semblance of a connection like we'd once had.  Instead, there was only this, like the father-daughter relationship distilled.  Not enough communication, barely any familiarity, both of us flooded with very different sorts of fear, confusion, and frustration.  I imagined it was much like the bonds that had kept primitive families together in an era when living from week to week was a challenge.  Basic, crude, but almost primeval.



She arrived, minutes later.  A woman, tall, in a suit, carrying nothing with her.  I sensed her at the periphery of my range, walking with a steady, strong stride.



I was reminded of the Siberian, almost.  The way she moved with the confidence of the indomitable, the way that she was almost careful as she moved among people.  Except that where the Siberian was only careful among her teammates, this woman was careful with everybody.



It took her five minutes to reach us, walking through the crowds, using the pedestrian crossings.



But the person I found myself comparing her to, as she approached the PRT building, wasn't the Siberian.  It was \emph{me}.  She reached her home ground, and people started to \emph{recognize} her.  They reacted, moving out of her way.  Showing respect.  Showing fear, in some cases.



Three of the Wards were in the elevator when it stopped at the ground floor.  Kid Win was taking his drone recharge station apart, which meant it was just Clockblocker, Crucible and Vista that crossed paths with her.



The Wards took only a moment to recognize her as she entered the elevator, and the two native Brocktonites left, pulling a protesting, confused Crucible after them.



In a matter of a minute, she was opening the door to the cell.  A woman, the sort who could be forty but looked like she was in her late twenties.  Hispanic, insofar as that was a descriptor, with darker skin and long, straight black hair.



But more than her description, the part of her that hit me was her \emph{presence}.  Almost without thinking about it, I got out of my chair, standing, the chains of my cuffs pulling taut against the lock on the table.  My lawyer, Miss Militia and Tagg all stood, my dad a step behind them, bewildered.  The only one not in the know.



``Chief Director,'' I said.



``\emph{Deputy }Chief.  I've stepped down from my position, but I still have to train my replacement,'' she said, her gaze piercing through me.  I couldn't even tell that one of her eyes was a prosthetic.  ``And seeing to some leftover crises.  \emph{Hello}, Ms. Hebert.''



She extended a hand.  As though driven to accept the handshake by a peculiar gravity, I extended my own hand and shook it.  Her firm grip could have pulverized me.  I might have been less intimidated if I were trapped in a small pen with an angry bull elephant.



``And Mr. Danny Hebert,'' she said.  She shook my father's hand.



Tagg stood from the chair at the table and moved over one left, leaving the seat for his superior.  ``Since you've made up your mind about staying, you'll need to know.  This is Deputy Chief Director Costa-Brown of the PRT.''



My father nodded.  I was getting the feeling he was almost shell-shocked.  To find out about the end of the world, the situation his daughter was in, and countless other things, the name of this woman might not have even processed for him.



``Otherwise known as Alexandria,'' Alexandria said, taking the chair opposite me.





