





I watched my dad's expression change.  ``I don't understand.''



``Like I said,'' Tagg said, ``Peace of mind.''



``Let's get started,'' Alexandria said.  ``I believe I'm fully up to speed, unless Director Tagg has agreed to any deals or made any concessions.''



``Sadly, he hasn't,'' my lawyer said.



``This is common knowledge?'' my dad murmured to me.



``Since roughly ten days ago,'' I said, not taking my eyes off the woman.  She was looking at me like Tattletale sometimes did.  It made me distinctly uncomfortable.



``Let's not make this the focus of our discussion.  You wanted to be on board, I presume.  You had to be informed, so you understood exactly what it means when I make a threat.''



``You're planning to make threats?'' I asked.



``Threats is the wrong word,'' she said.  ``But English is a limited language in some ways.  There's really no word to articulate what I mean.  A threat with a measure of inevitability to it.  A promise?  Too feeble.  People break promises too often.  A curse?  A malediction?  Too\ldots magical.  An oath?  The connotations are wrong.  When I say I'll do something, I make it happen.''



I didn't respond.  Mr. Calle did.  ``You seem rather confident.''



``\emph{Over}confident?  I imagine I seem that way.  It doesn't matter.''



I studied her, ``When you say you're going to do something?  What is it you're doing?''



``Putting an end to this nonsense, for one thing.  The PRT, flawed as it is, is my legacy, and I truly believe that it saves lives, or I wouldn't try to protect it.''



``\emph{I'm }trying to protect it,'' I said.



``I know,'' she said.  ``But the timing is wrong.  Things are too fragile at this moment.  It won't do.  We'll arrange this discussion for another time, weeks or months from now, when things have stabilized.''



``I\ldots don't think it works that way,'' I said.



``It does.  Truth be told, I've relinquished all authority.  I'm serving under the new Chief Director, and I'm carrying out his instructions, between the times where I'm instructing him in the particulars of his job.  \emph{Alexandria}, however, remains with the Protectorate, having given her notice that she quits within the week.  She'll continue as a solo operative.''



\emph{An operative for Cauldron}, I thought.  I didn't say it aloud.  Best to let her dictate what information was acceptable to mention aloud.  \emph{And she refers to her costumed self as someone else entirely}.



I could see the confusion in my father's face, the dawning realization of how far in over his head he was.



``So you're following orders,'' I said.  ``That's the worst and scariest excuse in the world, really.''



``It's a reality,'' she said.  ``When you're dealing with organizations as big as these.''



``And it's also a reality that you'll have people at the top who don't understand how things work on the ground, giving orders that don't jibe with reality.''



``You'd be surprised at what I'm capable of understanding,'' Alexandria told me.



``You're forgetting about the Undersiders.''



``No,'' she said.  ``I don't forget anything.  Your team is now \emph{my} bargaining chip.''



I narrowed my eyes.  ``How's that?''



``It's twenty minutes to six.  I'm not in a particular rush, and I actually enjoy the idea of some field work.  We can talk for five minutes, and then have `Alexandria' remove one of your teammates from the field.  Depending on the situation, I will either arrest them and take them to PRT offices in New York and Boston, or I'll kill them.''



I could feel my blood run cold.



``After, we can talk for another five or ten minutes, and then I will, again, depart to dispatch one of your teammates.  I expect that by the time the sun sets at eight thirty, the Undersiders will be either dealt with or so neutered that they aren't a consideration.''



``You're talking about killing teenagers,'' my dad said.  ``Without a trial?''



``I'm talking about self-defense, if it comes down to it.  Tattletale can see through weaknesses.  I can't imagine that she'd be able to leverage mine in the spur of the moment, but I won't rule anything out.''



I stared at her.  ``You're willing to go this far, yet you couldn't bring yourself to show up to fight the Slaughterhouse Nine.  Or Echidna, when she first showed.''



``There were extenuating circumstances.''



``Tattletale, you mean.''



``No.  Tattletale was only a small part of it,'' she said.  ``And it should be obvious that the rest isn't up for discussion.  Three minutes and forty-five seconds.  Negotiate.''



``You mean you want me to make concessions.''



``I'm saying I'm willing to hear you out.  Convince me.''



``You're underestimating my team.''



``And now you're referring to them as `your team'.  I thought you left.  You committed to this idea of yours, did you not?''



``You know what I mean.''



``I do.  But as much as I may be underestimating them, I find that others underestimate \emph{me}.  Strength, durability, flight.  It doesn't lend itself to much imagination, does it?  Yet others acknowledge me as one of the strongest heroes in the world.  `Cape geeks' debate my effectiveness, protesting that I'm only seen as powerful by association with Legend and Eidolon.  Do feel free to interrupt me if you want to talk about more concrete things.''



I would have, if I could have thought of something to say.



``My reputation isn't so different from yours, Taylor Hebert.  It's a reputation that was \emph{forged}.  There have been fifty-six Endbringer attacks in the last nineteen years.  I have personally participated in forty-nine of them, and in each fight I've attended, I've been in the thick of the fighting, personally trading blows with the abominations.  The creatures\emph{ know} me.  They know how to fight me, and I know how to fight them.  Yet I'm still here.  Strength, invulnerability, flight.  Those are my core powers, but my \emph{other} power is greater.''



``Other power?'' my dad asked.  ``I remember.  When you started off\ldots you explained the reason for your name.''



``A reference to the burned library of Alexandria.  It's been mythologized as that era's sum of human knowledge.  I am much the same.  I think faster, I think more \emph{easily}.  I know martial arts and I remember everything that crosses my path.''



Miss Militia reacted to that, giving Alexandria a look I couldn't interpret.



She went on.  ``I would say I am one of three or four people in this world who truly \emph{understands} what is going on.  I don't have all of the answers, and there are some riddles in particular that we're desperately seeking to unravel.''



``\emph{We}, of course, being\ldots'' I said, trailing off.  It wasn't a question.  Something about the gravity of the word made my dad look at me, startled.



``I won't discuss the others.  I've been disconnected from my former partners, so it's a moot point.  A \emph{debatable} point, to use the true meaning of the word.''



I saw a possible piece of leverage and grasped for it, ``If you need answers, then we're the last people you should be attacking.  Tattletale can offer input.  Leave the Undersiders in place, and they can work with you where necessary.  Treat me fairly, and I'm sure Tattletale will play ball.''



``There's two problems with that offer,'' Alexandria said.  She stood from her seat and adjusted her suit jacket, then turned her attention to her cuffs.  ``First of all, I believe I mentioned that there's only a small number of people who truly understand what's going on.  We haven't shared this information.  Why?''



I shook my head.  ``I don't know.''



``This isn't a riddle.  It's quite simple: we don't want people to know.  And we don't want people to know for \emph{good}\emph{reason}.  Having Tattletale off leash with all of the information she might discover is a dangerous prospect.''



``She's not that unpredictable.''



``But it's not a variable we can afford to have in play.  As I've said, things are fragile.  Which brings me to my second point.  There's no reason to leave her here if we can bring her into custody and use her freedom or \emph{probationary} freedom as leverage to obtain her talents.''



I frowned.



Alexandria glanced at Tagg, ``It's time.  Five forty-five.  I'll be back in ten minutes.''



\emph{Ten minutes}.



She was at the door, waiting for the guard to open it, when I called out, ``Tattletale won't listen.  She's too rebellious, wants to be the smartest person in the room.  If you force her, she'll sabotage you, or she'll just make you put her in the Birdcage, having her here, it's the only way to get her help.''



Alexandria paused, then looked back at me.  ``That will do.  Information I can use, that changes how I'll respond to this particular confrontation.  I don't agree, but we can discuss that after.  I'll target one of the others in the meantime.''



The metal door slammed shut.



Miss Militia stood.  ``I need some fresh air.''



She didn't ask for permission, and she didn't even look at anyone as she made her way to the door and knocked for the PRT guard to let her through.



``Everything she was talking about,'' my dad said, ``I can't wrap my head around this.''



``This is what I've been living,'' I said.  ``\emph{This }has been my day-to-day.  My friends and I, facing terminal risk, facing down monsters like \emph{her}, like Alexandria.''



``She's one of the \emph{heroes}.''



``Yeah,'' I said, meeting my dad's eyes.  It hadn't been so long ago that I'd been able to cling to that basic idea.  The \emph{image}, as I'd heard it phrased, of the heroes, of the Triumvirate.  It had been Armsmaster who instilled the seed of doubt in me, as far as the heroes went.  ``Do you think she's that heroic, now that you've met her in person?''



``No,'' he said.  He looked troubled.



Shit.  I was stuck in a box while one of the scariest heroes around was going after my friends.  I'd expected retaliation, had told Tattletale to expect it, but this was\ldots I hadn't expected \emph{Alexandria}.  She wasn't even supposed to be with the PRT.  Eidolon, we possibly could have dealt with.  Or Tattletale could have.  Even Legend, possibly.  Alexandria was something else.  The heroic equivalent of a cruise missile.



There was Grue's power, Imp's power\ldots did Alexandria have the ability to see through it?



Alexandria was taking her time.  She'd said ten minutes, but she wasn't in a hurry, making her way out of the building.



``You know, now,'' I said.  ``After the Echidna incident--''



I could see Tagg stiffen, kept talking, ``--\emph{Stuff} went down.  Alexandria was outed as head of the PRT, other secrets came to light.  You know the PRT is supposed to be led by non-capes, there was scandal, and now the PRT is falling apart.''



``I see,'' my dad said.  ``Other secrets?''



``You don't want to know,'' I said.  ``And Tagg would be \emph{exceedingly }upset if I shared.''



My dad frowned and stared down at the table.  ``I believe you.''



I nodded.



Alexandria had found an alley and promptly took to the air, zig-zagging between buildings and flying with enough speed that people couldn't follow her with their eyes.



``My phone isn't working,'' Mr. Calle said.



``Can't have you warning them,'' Tagg replied.



``I'm offended at the implication,'' Mr. Calle said.



``Can't have \emph{her} warning them either,'' Tagg replied.



\emph{Warning them}.  I needed a way to contact my team. Cells wouldn't work.  A land line?  An unoccupied office\ldots Tagg's office would do.  My bugs made their way there.



Too small to affect anything, to press a key on the computer, even if I could see the screen.  Too small to transmit a message of any sort.



I needed a larger bug.  There were larger beetles and cockroaches outside.  Everything else had been wiped out by Kid Win's drones.



I could see Mr. Calle and Tagg watching my dad and I, looking between us.  ``What?''



Mr. Calle answered, ``I've represented a lot of supervillains.  I can count on one hand the ones who had parents show up at their trial, let alone pre-trial.  When they did show up, half of them were a nightmare.  \emph{Bambina's} mother, for example, all of the worst aspects of a showbiz parent, but the kid's a vandal and a mass murderer.  Don't even get me started on how toxic \emph{that} dynamic was.  You two are civil with one another, at the very least.  That's\ldots something.  Hold onto it.''



``Hold onto it?'' Tagg commented, from the opposite end of the table.  ``I think you're forgetting your client's circumstances.''



Again, interjecting himself in between my dad and I.  Driving in wedges.  I felt a momentary urge to do something painful to him.



I couldn't rise to the bait, though.  I had to channel the anger.  Bugs were finding their way through vents and down hallways, spreading out so the two or three remaining drones couldn't eradicate them.



Others clustered on Tagg's phone.  Silk allowed multiple bugs to effectively `grip' the phone handle.  Larger bugs found their way under the base of it, wedging their bodies beneath as the pull on the cord tilted it.  A little bit of progress, driving in the wedge to make sure the phone didn't simply fall back into place.



``You're going to jail, Skitter,'' Tagg said.  ``And if you're very, \emph{very} lucky, it won't be the Birdcage or a death sentence.''



``She's a \emph{minor},'' my dad said.



``Doesn't matter,'' Mr. Calle sighed.



``Look at me, Tagg,'' I said.  ``You said you weren't going to underestimate me.  Do you really think I'm worried?  Do you think I would have surrendered if I didn't have\emph{ }confidence that I'd be able to manage?''



My dad was staring at me.



``No,'' he said.  ``I think you have a number of plans in the works.  But it doesn't matter.  Alexandria can out-think your plans, counter anything your Tattletale throws at us.



His phone handset fell from its perch, clattering across the keys before it fell from the desk, swinging.  I could see the flare of light on the phone, marking that the line was active.  I hoped there wasn't a secretary who'd notice.



I flew the largest beetle I had into the number pad, driving him into the number five.  The bugs on the mouthpiece heard a sound I took to be the answering beep.



Five again.  Second number in the sequence.



Not hard enough.  No beep.



Five \emph{again}.



Seven numbers.



The message that came through was odd, rhythmic somehow, though I couldn't make out the words.  \emph{A recording}.



I had to dial an outside line.



Eight numbers this time, starting with\ldots Nine.  It took a full minute to hit the buttons.



Nothing.



Eight numbers starting with eight\ldots  No.



Seven.



The call went through.  I got a response.



\emph{Please be Lisa.}



I tried buzzing out words.  It didn't feel like enough.



So I retired the abused beetle and set to using cockroaches.  My bugs felt the indents of the characters on the number pad.



Two, five, three, nine, two, six\ldots



The voice interrupted me.



The number of syllables was right.  She understood.  The numbers each corresponded to three possible letters, and each number pressed on the phone generated a different sound.  Anyone else might have struggled, but Tattletale picked up on it right away.  `Alexandria'.



I could only hope it helped.  A little forewarning, at best.



Still couldn't make out words that followed.  The filter of both the phone and my bugs was too much, and I couldn't begin to guess where the speaker phone button was.  Wasn't sure I wanted to risk using it in case someone stepped into the office.  A phone being off the hook was far better than a voice talking to nothing.



``You meant it, when you said they were your friends,'' my dad said.



``We've been through thick and thin.  They saved me, in some ways.  I'd like to think I saved them.''



Tagg snorted.  I ignored him.



``They did\ldots bad things, didn't they?'' my dad asked.



``So have I,'' I said.



``But you're willing to martyr yourself for them?''



``No,'' I said.  ``I didn't come here to be a martyr, I had other hopes.  But\ldots things didn't work out like that.  It's down to secondary goals\ldots and if \emph{those} fail, then I'm willing to go to jail for their sakes.  Not just my friends.  The people in my territory, and maybe just a little, \emph{everyone}.''



I looked at Tagg as I said that last word.  He gave me a dirty look, then more or less turned his attention to his phone, watching me with one eye while texting with one hand.



``Everyone?'' my dad asked.



``We can't lose the next Endbringer fight,'' was all I could say.



``No, I don't imagine we can,'' he said.



\emph{That} was something he understood in full, even if he didn't know the particulars.  The Endbringers were something we \emph{all} understood.  A fact of reality, something that touched \emph{everyone}, struck a chord of fear in cape and civilian alike.



My heart sank as Alexandria appeared.  She plunged past the cloud of bugs that had collected over the roof, into an opening aperture in the ceiling.  She passed down a shaft that ran parallel to the elevator, and into the Wards' quarters.



From there, she reached the elevator and made her way up to the cells.



Alexandria rejoined us in the cell, virtually the same, though her hair was disheveled, her suit jacket folded over one arm.  She laid it across the back of Miss Militia's empty chair and stayed there, leaning on the back of the chair that was bolted to the floor.



Noting Miss Militia's absence led to me double checking on her.  She was on the roof.  No, I couldn't count on anything from her.  I'd hoped to have one more piece in play, but she was leaning over a railing at the edge of a helicopter landing pad, staring out over the city.



Alexandria had to be my focus.  She was staring at me, scrutinizing me.  I met her eyes, and she locked hers onto mine.



``I'd thought Tattletale had figured it out\ldots'' she paused, ``But no.  You told them.  You have an open line of communication with them.''



I shrugged, thinking of Tagg's phone, with the handset still dangling over the edge of the desk.



Wished I could hear her response.  What had happened to my teammates?



``Let's take five minutes more to talk.  Then I'll take care of another of the Undersiders.''



``Another?''



``A PRT van will be along shortly.  I wanted to keep to my time commitment, so I sent a truck.''



``Why should I say anything?'' I asked her.



``Because as long as we're talking, I'm not out there, taking your team to pieces, and you have a shot at passing them information.  It gives them time to recuperate and strategize.  Five minutes gives them time to make a getaway, or contact help.  I imagine you arranged for backup.  Hired mercenaries to help break you out if this went badly enough that you faced jail without getting anything you wanted or needed.''



I set my jaw.



``I know the general value of the properties you acquired, the \emph{proposed} value of it.  Your team would spend it.  Ninety two million dollars, spent on hired soldiers, hired parahumans.  That's only your liquid assets.''



I didn't reply.  I set to typing the next message on Tagg's phone.  K-N-O-W-S-A-B-O-U-T-M-E-R-C-S



She straightened, removing her hands from the back of the chair.  ``If you're not going to say anything, I might as well go now.  You're rather partial to Grue, aren't you?  Or should I take Tattletale out of the picture?''



``We can talk,'' I told her.



``Excellent,'' she said.  She stepped around the corner of the table and sat in her chair, opposite me.  ``Do you need anything?  Water?  Coffee?  Soda?''



I shook my head.



``Mr. Calle?  Mr. Hebert?''



Two refusals.



She removed her phone from her jacket pocket.  ``Forgive me for using this in the midst of our discussion.  Chevalier is likely to become the head of the Protectorate once the Triumvirate has departed, and he's insisting that I keep tabs with him, what with the scandal and all.  I'd show you, but that would be a breach of confidence.''



She smiled, as though at a private joke.  The smile didn't matter to me.  It was the way her eyes didn't leave me.



``You're cold reading me,'' I said.



``Cold reading?'' My dad asked.



``Tattletale does it too.  Mixes details she knows with ones she doesn't, with very careful wording and a bit of an edge with her thinker powers.''



``Mm hmm,'' Alexandria said.  She typed expertly on her phone, almost absently.  ``I know you've probably got someone in the lobby or outside, receiving coded messages.  I know about the mercenaries.  \emph{More }mercenaries than I implied.  I expect Tattletale called in favors.  Probably not the Irregulars, but I didn't read that.  Simple logic.  They wouldn't work for you.  I know that you're still feeling confident, but not entirely so.  If you were very close to breaking or very, \emph{very} confident, you would have accepted my offer of a drink.  And I know that your bugs can't see computer screens.''



Was she bluffing on that last part?  Did it matter if she was?  I could refuse, play some kind of trick, and she'd see right through it.



``I could make some noise about my client's rights being trampled, a lack of consent to that kind of analysis,'' Mr. Calle said.



``But you know the law doesn't apply here.  We're in a gray area, up until the moment \emph{we} decide to press charges and set this into motion, or \emph{you} decide to force the issue.  But neither of us want that.  For now, this is\ldots somewhere between her being in our custody and us having a friendly chat.''



My lawyer glanced at me.  I frowned.  ``Yeah.  So long as she doesn't start grilling me.''



``As you wish,'' Mr. Calle said.



My head turned as I sensed the truck arriving.   Bugs clustered to it as it found a spot at the side of the building, PRT uniforms moving their target on a stretcher.  My bugs shifted position, tracking what they were moving.  The white mask, the curls, the shirt, with a tightly woven fabric beneath\ldots a spider silk shirt?  It was Regent, unconscious.



The bugs moved, tracing down the length of his arm.  It was broken in two places, virtually zig-zagging.  His leg was the same.  I caught the words `medical' and `doctor'.  `Tranquilizer'.



``He's arrived, I take it.'' Alexandria said.



I nodded tightly.



``The paradigm has changed,'' Alexandria said.  ``In\ldots two minutes and thirty seconds, I go and dispatch another of your teammates.  I'll hear concessions, offers or relevant information, and I'll adjust my methods and the severity of my attack where appropriate.''



``This is extortion,'' my dad said.



``She makes the process easier for us, we make it easier on her and her friends.''



I frowned.  ``That's still extortion.''



``Two minutes and eight seconds,'' she said, not even bothering to deny it.  She had the same habit as Tattletale, of knowing the time without looking at a clock.  ``They're going to be running, now, trying to throw me off their trail.  I'll find them.  I can study the environment, I've studied the case histories and I know where they own property.''



Another alert I needed to give.  I was still typing in the last one.  The cockroaches weren't strong enough to hit the keys with enough force, so it was more of a case of having to leverage the key down through the combined efforts of several larger roaches and carefully arranged silk.



I grit my teeth, trying to focus on the spelling while keeping track of what Alexandria was saying.  Started on the next message.  X-K-N-O-W-S-P-R-O-P-E-R-T-I-E-S



``You're backing me into a corner,'' I said.  ``Backing \emph{them} into a corner.  Someone's bound to snap.''



``Most likely,'' she said, and there wasn't a trace of concern in her expression.  It was almost eerie, how little she seemed to care.  Was that her passenger at work, or was she simply good enough at what she did, comfortable enough in her invincibility, that she'd grown able to shrug off the insignificant things?



I shook my head.  ``I'm not making concessions.  The terms I gave still stand.  If you want to discuss the reasons behind--''



She was already getting out of her chair.



``--behind why I made the demands I made, we can.  I think you'll find it reasonable.''



``I've heard this,'' Alexandria said.  She donned her suit jacket, buttoning it up in front.  ``Read it, rather.  I've thought about all the permutations and unless you're willing to change tack or tell me something I don't know, there's no point to this discussion.''



She walked to the door and knocked.  While waiting for the officer to open the door, she turned, ``One last chance to offer me something.  Any detail I can use, things to watch out for.''



\emph{Bitch}, I thought.  \emph{Her power, it screwed with her head}.  \emph{She can't relate to people.  She doesn't understand facial expressions, body language or our social constructs.  It's all replaced by dog behavior. }



\emph{Grue.  Post traumatic stress.  He doesn't like doctors, doesn't like being confined, or the dark.  But he's stable otherwise}.



\emph{Information that could be used to protect Bitch, protect Grue.  To keep a bad situation from getting worse.  }It felt like it would be a betrayal anyways.  It was an eerie reversal of the rationalization I'd done back at the bank robbery, on my first job as a villain.  Telling myself that terrorizing the hostages was for their own good.



But I couldn't bring myself to betray them on that level.  Not to people who trusted me.



And she was gone.



I grit my teeth.  I looked at Calle, but he shook his head.



Tagg reached for his phone, where it sat on the table.



Long minutes passed, as Tagg texted and I sat in anxious silence.



``You said you've worked with cape families,'' my dad spoke.  It took me a second to realize he was talking to Calle.



``Yes,'' my lawyer answered.



``Can I ask you some questions?''



``I was just about to step outside, call some colleagues.''



``Oh.''



``After.  Unless you want to join me?''



``Isn't it better if she isn't alone?''



``Everything's recorded.  Short of her being threatened with serious bodily injury or death, I don't see a problem.''



My dad cast me a look.  I nodded.



He left with Mr. Calle.



``You and I,'' Tagg said.



I folded my arms as best as I was able, then leaned forward to rest my head.  Not worth giving him the benefit of a conversation.



The table shook, and I briefly looked up, only to see Tagg setting his feet on the metal surface.



He took his time getting comfortable, and kicked the table several times in the process.



When I set my head down, he started humming.



\emph{He's trying to get to me}, I thought to myself, for the Nth time.



They were bullies.  Tagg and Alexandria both.  They were the equivalent of the older child picking on the kindergartener, or the adult picking on the child.  They had power to throw around that I didn't, they had freedom, liberty, the power of choice.  They wanted to punish me, to put me off-balance for their own ends.



Just\ldots bullies in a grander scale.



I simultaneously felt like I understood Tagg a little more, and a little less.



Mr. Calle answered a ton of my father's questions, big and small.  About things I'd thought were common knowledge, like trigger events, and more specific, grave matters, like the prospect of my receiving the death penalty.  When he'd exhausted each of those questions, he asked about other things.  \emph{Smarter} things, like the degree to which he might be able to stand up to Alexandria or Tagg, about how he could work with Calle to throw them off-balance, and signals to arrange a plan of attack.



My dad, entirely out of place, out of his depth, confused and utterly unarmed, fighting to get up to speed, in the hopes that he could do something to help.



It was a step forward.  A small step, but a step forward.



Tagg stood, approaching me, then leaned on the table just beside me, so he loomed over me, not speaking, invading my personal space, denying me the ability to rest or relax.



And my bugs, in his office, continued punching away as best as they were able.  Me, communicating with Tattletale, unable to hear her response, straining to hear some sign of the violence.  Had they split up?



Regent's arms and legs had been set, and he lay on a bed identical to the one I'd had, apparently tranquilized.



I was the target, the mastermind, the one they were trying to break.



Alexandria only took six minutes.  She arrived by the same route, only she held a girl this time.  A hard mask with horns and slanted lenses that tapered into points at the corners, a skin-tight bodysuit.  Imp.



Alexandria had found a way around Imp's power.  Or her mental powers had overridden them.



One more body in the cells.  One more Undersider down.



Alexandria found her way back to the cells before my dad and my lawyer did, accompanied by Miss Militia.  Alexandria grabbed one of Kid Win's active drones from the air and tucked it under one arm like a football as she made her way down, and held it up as she visited the cell where they were checking an unconscious, tranquilized Imp.  Every bug was eradicated by the mist that appeared, leaving me utterly blind.



I didn't see her again until she opened the door and joined us.  She was drenched, her hair soaked, swept back away from her face, and the makeup that had hidden the seam of her prosthetic eye had been washed away, leaving a conspicuous line in place.  Miss Militia looked grim and very dry beside her.



``They fought back?''  I asked.



``A firehose, and a cape with a water geyser power.  They tried to drown me.  It didn't work.  Others have tried the same thing, in many different variations.  Old hat.''



A cape with water generating powers?  \emph{The Ambassadors}.



She looked around, ``Your lawyer?''



``Out,'' Tagg said, not looking up from his phone.



``I suppose it would be bad manners to talk to you while he's occupied,'' Alexandria said.



I didn't reply.



``Well, five minutes before I go again.  If this is a delaying tactic, it won't work.''



``Read my face,'' I said, ``It's not a delaying tactic.''



``It doesn't matter,'' she said.  ``I'm keeping to a schedule.  Roughly half an hour at a time, collecting one Undersider with each excursion.  I told you I'd hold off on collecting Tattletale, so I'll save her for last.  Four minutes and forty seconds.''



Tattletale was still periodically speaking into the phone, while I typed out letters.  She'd stopped talking as much when I'd typed out a few words to let her know I couldn't understand.  No, her focus right now would be on arranging her remaining forces, handling what she could, dealing with Alexandria.



``I'd like to stay,'' Alexandria said.  ``May I sit?''



``If you want,'' I said.  I gestured towards the chair, best as I was able with the cuffs.



``Excellent.  So cooperative.''  She sat down.  ``And we can talk?''



I nodded mutely.



Alexandria, a bully, believing herself untouchable.  I felt a grim sort of loathing stirring in the depths of my gut.



``My terms, to you.  You surrender.  The Undersiders receive no amnesty, but I let captives go, with all required medical care.  They fend for themselves from here on out.  Tagg remains in position.  He's here for a reason.  Miss Militia is promoted elsewhere.  With the fall of the Triumvirate, we need a new core group.  We can market it.''



``That's not what I wanted.''



``It's what I'm offering.  And you\ldots provided you cooperate fully, giving us all the information we desire on you, your histories, and the Undersiders, we put you in juvenile detention.  Two years, followed by a long probation and acknowledgement that \emph{any} conceivable violation of that probation will be counted as a third strike and cause for sentencing to the Birdcage.''



My dad and lawyer were just arriving.



``What's this?'' Mr. Calle asked.



``Skitter's hearing my revised terms,'' Alexandria said.



``And?'' Mr. Calle asked.



``They want me to turn myself in.  I get virtually nothing, except the prompt release of the Undersiders she's picked up and a stay in juvenile detention until I'm eighteen.''



I could see my dad's eyes light up.  He saw this as a way out, when he was seeing just how deep we were in the midst of this.



Which broke my heart, in a way.



``And your thoughts?'' Mr. Calle asked.



``No,'' I said.  I looked at Alexandria.  ``No.''



``This isn't the sort of offer that stays on the table,'' she said.  ``If you want to push this further, we could \emph{keep} the Undersiders.''



``You \emph{need} the Undersiders,'' I told her.  ``You need someone on the ground, keeping the \emph{real} monsters out of the city.  You \emph{need} us, so don't pretend you're really going to keep them.''



``There's other options,'' she said.



``It doesn't matter,'' I said, ``Because even if there wasn't that security, \emph{no}.''



``That's a disappointment,'' she said.



``You wanted compromise, Skitter,'' Miss Militia said, ``But you're asking for the impossible.''



``I'm asking for the \emph{improbable,'' }I said.  ``But it wouldn't be worth fighting for if it was easy.  Alexandria isn't asking me to meet her halfway.  She's threatening people I love.''



``From teammates to friends to people you love.''



I grit my teeth.



``I don't blame you,'' she said.  ``I loved Hero.  I loved Legend, and Eidolon, and Myrddin.  I know what it means to pass through hell together, to take a desperate breath for air, to clutch for clarity of mind, and help each other find the briefest of respite in the little things, only to plunge into that hell once more.  The little jokes, the familiarity, the gestures and small kindnesses, they count for a lot, when you've been through what we've been through--''



``Don't compare us,'' I cut in.



``--and you learn to look past their faults.  The little evils,'' she said.  ``And they learn to look past yours.''



Miss Militia gave Alexandria a curious look, then turned to me, ``The offer, it's the most reasonable one we can give you.  It's \emph{generous}, considering all you've done.''



``It's not enough,'' I said.  ``Until my team has amnesty, I can't back down.  I can't abandon them to fight lunatics like Tagg and Alexandria the second I'm gone.''



``That's what you want?'' Alexandria asked.  ``Amnesty, release for captured teammates, and a sentence to juvenile detention?''



My dad reached out, taking my hand, a silent plea.  Saying everything without doing me the disservice of interjecting.



It wasn't enough, but it was something.  I could trust my teammates to hold their own.  I could\ldots I could find my way.  Two years made for such a small length of time.  It\ldots it would mean I was in custody when Dinah's deadline came.  But maybe that was what she'd wanted.  For me to be somewhere secure when it all started.  I couldn't rule it out.



And all it would take was for me to do what I'd done for so long before I had my powers, for months \emph{after} I'd had my powers.  To capitulate, to let go of my pride.  To let \emph{them }win, those people who wanted to use their power, their prestige and superiority against me.



My dad squeezed my hand, hard.



``I named my terms,'' I told Alexandria.  ``I trust my teammates, and I trust that they'll win where it counts.  No.''



I met Tagg's eyes, and my voice was a growl, ``And if you fucking hurt another hair on their heads, I'll see you pay for it.  Like Lung, like Valefor, and if it comes down to it, I'll come after you like I did with Butcher, and Coil- Calvert.''



I directed my glare at Alexandria as I said that last part.



``You're admitting--'' Miss Militia started.



``Let's not pretend we don't all know,'' I said.



I felt my dad's hand drop away from mine.  I might have met his eyes, to take in the hurt and the pain that came with seeing who I really was, but I wasn't willing to break eye contact with Alexandria.



\emph{You can read facial expressions?  Read this.  Know I'm telling the truth}.  \emph{Know that I'll take you apart, given the slightest excuse.}



I was pressing the keys on the telephone before Alexandria had even stood from her seat.  Another warning that Alexandria was en route.



She stood, wordless.  There was no negotiation, no offer for leniency, and I didn't ask for either.



I could only hope.



In a matter of minutes, she was gone, flying away.  A third mission.  A third hunt.



Bugs found their way through vents to Regent, but Imp's cell was sealed tight, no doubt due to the Stranger-class precautions that had led to the note being pasted on her cell door, notifying the PRT of the special precautions.  It didn't matter.  Regent was still unconscious, and Imp was likely to be as well.



Grue, Rachel, Tattletale and Parian.  Flechette too, if it came down to it.



Flechette\ldots could she hurt Alexandria?



It didn't matter.  I didn't have answers, couldn't get them.  I could only wait, keeping my bugs out of the way of the drones that Kid Win had finally recharged.



``You had a way out,'' Miss Militia said.



``You said you understand me,'' I told her.  ``That you had insight into who I was as a person, now that you knew my history.  If that's true, you understand why I had to say no.''



``For your sake.  Because of what you've been through.''



``And because of \emph{them}.  They'd never forgive me if I betrayed everything they helped me become, because I didn't think they could fend for themselves.''



``And me?'' my dad asked.  ``I know it's asking a lot.  I failed you where it counted.''



``Dad--''



``And maybe it's selfish, to want my daughter, when you're talking about things on this scale\ldots'' he said, pausing as if he was going to follow that with an argument.  But no argument followed.



And I couldn't give him a good response.



Eight minutes passed.  I could count the progression of time on the clock hands, when I dared let a bug pass through open spaces.



Nine minutes in, I could see Tagg suddenly tense, lines in his neck standing out as he read the newest message on his phone.  He glanced at me, but he didn't say anything and I didn't ask.



The PRT van arrived before Alexandria did, this time.  The PRT officers took their time before they finally emerged.



Restless, I shifted position.  My forearms were digging into the table where the cuffs held my arms in front of me.  Leaning forward made my back hurt.



They opened the back of the van, and there were no precautions this time.  Their weapons were holstered, and they didn't stand in any particular formation.



The only thing in the back was a single body bag.



Back pain forgotten, I went as stiff as Tagg.  I drew more bugs in to get a better picture of the scene.



They took a different route this time, using their phones to make their way through the various doors and checkpoints.  They entered the attached building.  A small hospital, or a special office with medical facilities.  It didn't matter.



And they made their way to the morgue.



The size of the bag\ldots it couldn't be Lizardtail.  He was too large.  Was the wrong size and shape to be one of the dogs.  That left only three real possibilities.  A PRT officer, Rachel, or Brian.



I closed my eyes, clenched my hands.



Then one of the PRT officers who was escorting the body said something, and others laughed in response.  It was one of those rare moments I could discern tone, and it wasn't a kind one.  That was enough for me to know it wasn't one of them.  It wasn't a civilian.



Metal clicked as they unlocked the heavy clasps and locks that were likely meant to prevent any parahumans from getting up from the dead.



They unzipped the bag, and lifted the body onto the drawer.  The drawer slid into the recess, the lid was closed and locked.



I didn't want to know which of them it was.  I couldn't. Whether it was Brian or Rachel, it didn't matter.  Neither of them would get up from the dead.  They weren't so lucky.



I stared down at my hands, and I felt myself go cold, my thoughts crystal clear, singular.



``Taylor,'' my dad murmured, so quiet I could barely hear him.



``Yes?''



I sounded so calm, like an entirely different person was speaking.



``You're shaking,'' he whispered.



``Oh,'' I said.  I couldn't really think of anything else to say.  He was right.  My fingers were trembling.



I looked at Tagg, to see if he'd heard or if he'd noticed.  No indication, but his hand was close to his gun.  The text he'd read\ldots he \emph{knew}.  He probably wasn't aware he was doing it, but he was ready for a fight to erupt any second.



Miss Militia's hand wasn't, but I could read a tension in her, as she exchanged words with Calle.  But then, I suspected she could draw faster than Tagg in virtually any circumstance.  Or maybe she wasn't as ready or willing to deal out violence as Tagg was.



Then I had to lower my eyes, to hide the tears that were welling.  Needed just a few moments.  Just a few more seconds.



Alexandria arrived the same way she had after her last two excursions, through the hole in the roof.  With the speed she moved, she didn't risk being spotted.  Even photography wasn't in the cards.



With the speed she moved, she didn't seem to notice the bugs that followed after her as the aperture began to close behind her.



She got as far as the Wards HQ before she stopped and the bugs had a chance to catch up to her.



As though I'd thrown a javelin, they speared right for her nose and open mouth, the fastest moving bugs I had at my disposal, and spiders.



She was invincible, the flesh inside her throat untouchable.  The flap that kept food out of her lungs kept the bugs at bay.  At first.  They bound themselves together, spiders fixing themselves and others to the inside of her throat with adhesive.



As strong as she was, air didn't move past the mass of bugs that filled her mouth, as they \emph{fought }to move into positions where they could block her throat.  She coughed in an instinctive attempt to dislodge them.



Even with super strength, even with a diaphragm like hers, the coughs didn't remove every bug, and the greedy gasp of air allowed those who remained to find their way inside, filling her lungs.  They were just as impervious inside, but the bugs arranged themselves side by side, forming a layer that blocked the flow of oxygen to the membranes of the lung itself.  Spiders drew out silk, filling gaps.



If she could choke, if Leviathan saw submerging her in water as a viable tactic, if Tattletale saw fit to try to do the same, then I could drown her in insects.



The Wards were watching, realizing what was going on.  Clockblocker ran, pressing a button for the alarm.



And in front of me, Tagg moved, drawing his gun.  His voice was a roar, ``She knows!''



A thread caught it before he could point it at me, and it fell to the ground.



With each entry that had been made into the interrogation room, barring the one where she'd used the drone in Imp's cell, I'd brought more bugs inside.  Spiders, hornets, black widows, brown recluses and more.



I'd warned him.  He jumped as he felt the bites.  Shouted as hornets found the soft tissues of his eyes, his tongue and eardrums.  Black widows and brown recluses found crevices.



Miss Militia moved too, but the silk I'd used only bound her hand, didn't serve to stop her.



``Taylor!'' my dad's voice sounded so far away.



I'd promised myself I wouldn't let the bullies win again, I thought.  That I'd stop the monsters.



But the thoughts sounded disconnected, false.



No, this was revenge.  Something simpler than any of that.



Miss Militia raised a gun, pointing it at me, where I had my head bowed, hands still chained in front of me.  My dad was shaking me, but I wasn't a hard target to hurt.



And my bugs weren't hurting her.  Weren't touching my dad, or Mr. Calle, who was backed up into a corner, trying to make as much distance from me as he could.



She didn't shoot.  Her gun clattered to the ground.



``Taylor!'' she called out, as if she could reach me that way.  ``I'm not going to shoot, but you have to stop!''



``Not a promise, not an oath, or a malediction or a curse,'' I said, sounding calm, probably inaudible in the midst of Tagg's screaming.  ``Inevitable.  Wasn't that how she put it?  I told them.  Warned them.''



Alexandria, in the basement, still choking, drowning on dry land with lungs full of dragonflies, spiders and cockroaches, soared.  She flew through the closed barrier in the roof, and debris showered down on the Wards who'd approached her, wanting to help but finding themselves unable.



In moments, she was out of my range, too high in the air.  I wasn't sure it mattered.



And Tagg- Tagg was staggering towards me, roaring something incoherent, chewing and spitting in a feeble attempt to remove bugs from his mouth.  His tongue was likely swollen already.  The black widow venom would take effect soon.



He tried to push my dad out of the way, and my dad blocked him, shielding me with his body.



Tagg kicked my father hard enough to drive him to the ground.  The Director was still shouting, nearly blind.  He gripped me by the hair and slammed my head down on the table, hard.



I saw stars, felt tears welling out freely, as if the dam had finally broken.



Blind, writhing in pain and a struggle to get the insects off him, Tagg still managed to hold me down as the PRT officers burst into the room.  They had darts like the one that Shadow Stalker had kept in her crossbow, jammed one into my neck.



I had only the chance to think of how they'd just signed Tagg's death warrant, that my power would work while I was unconscious.  I could have rescinded the order in the last moments.  I didn't.



And then it was only darkness.  Oblivion.  A false kind of death.





