





\emph{Abandoned}.



The word hit me before I was fully conscious, as though my brain had grasped the idea before I even had half of a brain functioning.



My father, gone.  My lawyer was gone as well.  Not such a big surprise.  I'd gone all out, held little back, and I'd given no apparent justification.  To them, to my dad especially, I would have looked like a monster.



Fitting, because I'd been one.  I was one.  Was that a label that was affixed to me permanently, now?



My mind was wandering more than it should have.  My head hurt.  I tried to focus, turning to my bugs.



Except my \emph{swarm} was nearly gone.  Only a small fraction remained.  Hundreds, if that.  My bugs had carried out the last order I'd given them, to attack, before I was knocked out.  I knew that.  What confused me were the other behaviors my bugs had performed.



They'd spread out and searched my surroundings, and they'd been gunned down en masse by Kid Win's drones. I could sort of understand that, especially if they were actively searching for the last targets I'd given them. That, and I could picture myself unconsciously wanting to check for incoming threats and assess the battlefield before the tranquilizer took hold.  Odd, fucking inconvenient, but understandable.



But the fact that bugs had spent the time I was out to weave lengths of silk cord?  That was unusual, something out of place.  It was something I'd taken to having my bugs handle in the background at any given moment, but why would I carry it out in my sleep?  I was \emph{pretty} sure I hadn't given that order, which left only three real possibilities.  Either my unconscious mind had willed it while I slept, or my passenger had.  Unnerving.



More unnerving was the third possibility – that there wasn't a real distinction between my unconscious mind and the passenger.



I sat up, contorted in pain as I felt bruises and cuts making themselves known, and then groaned as my expression shifted and I felt the damage above and around my eye.  There was a wound: my skin had split, and the tightness coupled with the crusty wet sensation suggested drying blood.



My glasses were screwed up too.  Tagg had knocked one lens out of the frame when he'd slammed my face into the table.  My vision was oddly dreamlike, blurry through my right eye, too crisp through my left.  I moved my hands to move the glasses, and felt the heavy-duty cuffs encasing them.  The sort of handcuffs reserved for low-level Brutes, that covered my hands entirely, each hand welded to the other.



I was in the PRT offices.  I was back in my cell.



As far as I could tell, the building was empty.  My power reached five blocks, and\ldots nothing.  There were no people. Computers were active, television screens were glowing with shifting images, and cars sat in the middle of the road outside, but the people were gone.



Evacuation?  When my power hadn't stopped, the PRT would have ordered people to clear out of the area.



Maybe they weren't sure if my power would keep going if they shot me.



I stood and rolled my shoulders, feeling things pop, grind and sing with pain in response to the movement.  I'd had my hands fixed in front of me for the better part of the day, with only a brief respite in my cell while I'd showered.



Showering\ldots it made me think of being in my lair after the first night I'd \emph{been} with Brian.



I pushed it out of my mind, and Rachel appeared instead, stepping to fill the blank in my mind's eye.



As if I were suddenly \emph{channeling} her, I struck at the door with the restraints that encased my hands.  Metal struck metal, the strike barely denting the brushed stainless steel of the door's surface.



A rapid, high-pitched beeping sounded from above me.  I looked up at the orb just in time to see it lighting up.  I threw myself to the ground, felt the shock jolt through me.



If I'd been sore before, the jolt cranked it up to ten.  I felt my mind go white, heat coiling through the interior of my body, as though it were dancing around my internal organs and bones.  The strength went out of me; my cuffs were too heavy, and I didn't have the ability to hold them up.  I fell, as though the restraints were an anchor pulling me down.



I could feel my muscles twitching in a way that seemed like it was \emph{intentionally} making the sorest parts of me move.



``\emph{Do not disturb the peace of your cell.  This deterrence measure was calculated at twenty percent of your overall capacity.  The next response will be at twice the strength.  Thank you,'' }the automated voice informed me.



For long minutes, I lay there, spasming and searching the building with surviving bugs, because doing anything else was impossible or futile.



Needed out.



How had they unlocked my cell and the interrogation room?  They'd had phones.  PRT issue, probably, and had tapped the phone against the wall.



Phones\ldots there were no PRT officers in the building.



In the morgue\ldots there was a body bag.  Bugs clung to it.



Brian?  Rachel?  Someone else?



I sent bugs over to explore it.  One centipede to latch the zipper, other bugs to haul it back.



It was Tagg, dead.



I'd killed a man, and I had done it with my power, which somehow felt more intimate than the gun that killed Coil.  My power made the bugs an extension of myself, and I'd used them to murder the man.  It was little different from wrapping my hands around his throat and squeezing, or biting him in the throat and tearing deep enough that he couldn't survive.



I couldn't bring myself to feel anything meaningful about it.  I \emph{wanted} to.  I wanted to think of his daughters, apparently college students overseas, and his apparently loving wife, and the fact that I'd just taken a member of their family from them, much as my mom had been taken from me.  I wanted to feel \emph{terrible, }to cry, but I couldn't bring myself to.  I felt bad, but not as bad as I should have.



No.  I could only see the bully, the monster, the threat he posed to the city or the world.  To my team.



Or was that the threat he \emph{had} posed?  Was it too late to save them?



I couldn't check the time without sacrificing bugs to the patrolling drones.  However long I'd been out, the remainder of the Undersiders could be embroiled in an all-out war.



\emph{Tagg},  I thought.  \emph{Have to focus}.



His phone was in his jacket pocket, his key ring in his pants pocket.  Getting the items to me would be harder.  There were closed doors, vents, the elevator and the blocked elevator shaft.  The morgue was in a separate building, joined to the PRT office at one corner.



Worse, the numerous skirmishes in, outside and around the building had led to there being a great deal of renovation and rebuilding.  \emph{New} things were that much harder to get bugs through.  There were no open grates, no gaps in air conditioning ducts or anything in that vein.



There had to be a way.  I was down to a few hundred bugs.  Barely enough to matter.  I wasn't about to brute force my way through anything.



I thought of the hole Alexandria had put in the roof during her hurried exit.  It was the most indirect way, getting bugs from the basement of one building outside, to the roof, and back down to the basement of the next building\ldots but it was a path.  If there were barriers I wasn't sensing, I'd handle them.



Working together, bugs began dragging the keys and smart phone down the hall to the mortician's office.  Windows, squat, looked out at the parking lot, no doubt intended more to bring natural light into the office than for the sake of the view.  I knew before approaching them that the windows were open – there was fresh air flowing into the hallway, and my bugs could sense the shifting air currents.



A screen blocked the way.  Not a serious issue.  The bugs started chewing through the individual wires, while the bugs with the phone and key ring began binding the items in silk, connecting them to a line.



Minutes passed while the bugs made their way up to the hole in the roof, down the shaft to the Wards headquarters one floor below me, and to the elevator.



The stairwell was blocked off, the elevator\ldots the buttons.



I had the largest bug ram it.



Nothing.  Feeble at best.



The wiring.  Could I hotwire it like someone hotwired a car?



Getting into the walls wasn't as hard as it should have been.  Rachel had done a little damage when she'd attacked with the dogs a week ago.  Even though they'd shored it up and sealed the exterior from the interior, there were gaps that I could use to get inside from the building's interior, much as I'd done when disconnecting the outlet for Kid Win's drone recharging station.



The actual connection\ldots the damn thing seemed to be reinforced, with thick wires and a button mechanism that was too heavy to move from within.  The bugs themselves couldn't form a live connection between the button and the contact.



\emph{A workaround}.  I used cockroaches to carefully strip away insulation, two centipedes positioning themselves so their mandibles were above two respective pieces of wire, their tail ends entwined with one another.  Then they let themselves drop.  Their bodies bridged the gap between the wire behind the contact and the wiring by the button.



The centipedes died in an instant, and the door opened.



I dragged the smart phone and keys in, being careful to use bugs to bridge the gap so the phone and the keys wouldn't fall through, and then let the elevator carry the bugs to the floor above.  The doors opened automatically as the elevator arrived, and I brought the items out the same way.



The bugs began the slow process of bringing the phone to a point high enough on the wall.  I spent the time recovering, flexing my muscles until I was sure they moved right.  I had to draw out more silk to have a line strong enough, and set to reeling it in, anchoring end at the corner of the door frame, pushing up with the bugs and looping any slack around the corner of metal.



It wasn't halfway up when the heroes arrived to collect their prisoner.  A vibration through the building as a heavy vehicle landed on the helicopter pad on the roof.  Four legged, with turbines in the place of wings, and a neckless head.  A man stepped out.  Defiant.



Dragon arrived as Defiant reached the elevator door on the rooftop.  My bugs inside continued the glacial process of raising the phone to the necessary height, while the ones outside clustered on Defiant and Dragon.  They knew I was here.  There was no reason to be subtle.  The only thing I had to be careful of was keeping Defiant from killing the swarm with one of his bug zapping tricks.



His focus was on his phone and the door, instead.  He was typing something.  A password?



If one was required to access the phone, I was screwed.  If it was access specific\ldots



I memorized the sequence.  Now I had the problem of using it on the touch screen of the smart phone.



If it was pressure sensitive, then I could use it.



If it was heat-sensitive\ldots



Bugs approached the fluorescent lightbulbs in the hallway outside, warming themselves until their wings and legs threatened to burn up.



The pair of heroes was halfway to the elevator on the top floor when the phone reached the correct height.  Bugs I'd warmed on the bulbs moved to the keyboard, copying the same sequence of movements I'd tracked with the bugs on Defiant's glove and phone.



The door slid open.



I dropped to my hands and knees to get the phone in my teeth, stooped down so the bugs with the keys could latch on to my gauntlet-restraints, then speed-hobbled for the elevator, chains at my ankles clanking.



I hit the button a second before Defiant hit the one on the top floor.  The doors opened immediately.



They hadn't reacted yet.  The delay before the elevator moved hadn't registered with them.  Once they saw the elevator moving\ldots they would expect me to run, cut me off.



\emph{Fuck that}.



Had to second guess them, which was harder than it sounded, because they weren't dumb.  If they expected me to make a break for the ground floor, I'd have to do something else.



I leaned back against the wall and used my bare toe to hit the button for the first and third floors.  That done, I turned my attention to the keys.  The phone went into one pocket, moved by a swarm of bugs and the slope of my arm.  When that was done, smaller bugs searched the keyhole at the base of my restraints to gauge the width.  Other bugs marked the keys that fit the same size, yet others holding the ring against my restraints so I could use my teeth to pick through them, sliding them around the ring when they weren't appropriate.  Cockroaches wedged themselves in between keys to speed the process along.



Defiant and Dragon were moving.  Dragon opened a window and moved outside, while Defiant headed into the stairwell.  They wanted to cut me off on the ground floor.



They could communicate without talking.  Some kind of system built into their masks.  It made this harder.  I couldn't listen in and anticipate what they were saying.



By the time I passed the first floor, they were turning around.  I hurried to the stairwell, and took the stairs two at a time in a hurry to get up to the second floor.



Just inside the door, I used my toes to ease it closed, then crouched to stay out of sight as Dragon patrolled outside, peeking in the windows.



I tried a key, sliding it into the hole before successfully turning it with my teeth.  My lips came in contact with the cockroaches I was using to guide the metal into place.  I didn't care.



Disease, filth, disgust, they all came in a distant second to other priorities.  I felt numb, and it wasn't the electrocution.  They'd taken away someone important to me, \emph{pushed} me.  My dad was gone, my lawyer, my team\ldots my team wasn't here.



I wasn't sure I wanted to know why they hadn't come to the rescue, or why the mercenaries we'd hired hadn't been called in.



I had an ugly feeling in my gut that something was \emph{wrong}.  Something beyond what had just happened here, beyond the possibility that someone I loved, romantically or platonically, was gone.



I got the cuffs off, set them down on a computer chair and slid it neatly under the desk so the cuffs wouldn't be immediately apparent.



My hands were free.  I needed tools and I needed weapons.



I scooped up silk cords from the floor, where they'd been abandoned by the bugs that had been working on them.  Not much.  Most were short, but it was \emph{something}.  I set my bugs to splicing them together.  One twenty-foot rope was more use to me than ten cords that were each two or three feet long.



Other priorities.  \emph{Those fucking drones}.  I could see them, footballs with one end sawn off, carried aloft by antigravity panels like the ones from Kid Win's skateboard.  I could see one switch modes, unfolding and reconfiguring to an entirely different setup, from white to red.



I used my body to block its line of sight to my swarm, trusting that it wouldn't do any serious damage if there was a human in its line of sight, then grabbed the thing out of the air and shoved it into a desk drawer.  I shut the drawer firmly before blocking it with a box of paperwork.



I'd slipped out of the pair's grasp for just a moment.  I had little doubt they'd pull some other solution out of their tinker caps before long.  I crossed the room to get to a second drone, picking up a trash can from beside one desk, catching it like I might a large butterfly in a net, and then planting it on the ground, moving a monitor from someone's desk to sit on top.



Once the way was clear, my swarm worked to catch up.  Tagg's phone wasn't good for anything more than access until I figured out his password.  A check of the phones failed to give me a dial tone.  Dragon's work?



This floor was where the PRT officers worked.  It was where they got briefed and debriefed, and where they typed up their paperwork.  I'd observed them at work with my bugs, had seen the patterns and figured it out in advance.  I'd also seen where they kept their stuff.



Tagg's phone and the code Defiant had used served to open the supply room.  In the same moment the lock opened, Dragon turned around and made a beeline for the stairwell, using her jetpack to pick up speed.  Defiant changed direction only a moment later.



She'd tapped into the security system, no doubt.  Defiant would know the building's layout if he had any of his old technology.  I couldn't give them any advantages, and if she had eyes on the security system, it would eliminate any possibility of me evading them.  I set bugs to chewing on the lines that fed into the building from outside.



The boxes were locked, but I had Tagg's keys and nothing to lose.  Fully aware of Dragon and Defiant's approach, I worked my way through the keys in much the same way I had with the keys for the cuffs.



The lights abruptly went out.  After a moment, the lights came back on, with a dim red glow.  The backup generator.  I started to work on that as well.  I could fight in darkness.  I wasn't sure they could.



I could \emph{hear} them walking by the time I got the box open.



Grenade launchers, with special shells.  I turned a grenade launcher over in my hands before figuring out how to open it and load the cartridges.  Each was color coded, with a symbol and two-letter code stenciled on it.  A green cartridge with a face, eyes squinting, mouth open with tongue extended, T.G. beneath.  A red cartridge with the letters I.G. and a flame.  A blue cartridge with a stick-man stuck in goop, C.F. no doubt standing for containment foam.  A yellow cartridge with a lightning bolt and E.M. beneath.



I loaded the last, aiming out the open door of the storage area, and pulled the trigger.



Nothing.



A bar of black on the back of the grip lit up with letters, running vertically from above my thumb to the bottom of the grip.  `NONCONFIRMED'.



They'd either learned since we attacked the fundraiser, or they took stricter measures with their more dangerous weaponry.



I investigated, but there didn't seem to be a place to input any code.



The footsteps drew closer, heavy.  I could sense Defiant with my swarm, only a short distance away, looking into the briefing room to see if he could spot me.



\emph{Fingerprints}, I thought.  Except there wasn't a flat panel to press the finger against.  The grip was textured, and nothing about the barrel suggested it was meant to read anything.



\emph{The gloves}.



I used the same key that had opened the box to access the locker with the armor the PRT officers wore.  I found a glove and began pulling it on.



Defiant appeared in the doorway.  He aimed the butt of his spear at me, and the display on the gun dissipated.



He lunged, and the butt of his spear caught me just below the collarbone.  With that alone, he pushed me into the lockers with enough force that they rocked against my back, rendering me pinned.



I let the grenade launcher fall to the ground.



Dragon appeared behind him, setting one hand on his arm as she passed through the door.  He eased back on the pressure.



I glared at them, but they didn't speak, and Defiant didn't move to release me.  Were they talking with one another?



``Fine,'' I said.  ``You got me.  I had to--''



Defiant was shaking his head.  He tapped his mask.



Bugs flowed over the outside of his armor, and he didn't seem to mind.  There were no openings, no apertures, no air holes or gaps I could work a bug into.  He was playing the same game Mannequin had, to counteract my power.  Fuck it.  I wouldn't be able to sting him.  Dragon either, apparently.



He couldn't talk.  I wasn't positive he could even \emph{hear}.



He shifted his grip, then grabbed my upper left arm.  Dragon took hold of the right.  They half-walked, half-carried me towards the stairwells and elevator.  I walked more to keep them from putting more strain on my already sore shoulders than out of any need.  Their grip left me little doubt they could have held me off the ground if they wanted.



Defiant stopped mid-stride, then glanced at Dragon and me.



Without letting go of me he charged the very air with a current from his spear, frying each and every one of the bugs I had in the area.  It included, unfortunately, the two groups of bugs that were following me, each group discreetly escorting specialized canisters from the grenade launcher.  I could feel my hair shift in reaction to the strike, the little hairs on my arms and the nape of my neck standing to attention.



I wasn't sure if it would have worked, but my hope had been to possibly drop the grenades from overhead after we'd reached the roof.  No such luck.  I hung my head as we entered the stairwell, making our way up to the roof and the waiting vehicle.



This was my escort, apparently.  Heroes with the tools to disable and defeat my most common methods, sealed in suits that my bugs couldn't touch, overloaded with firepower, while I had none.



Unfair.  All of it.  On so many levels.  Too many situations, all together, with no perfect, \emph{right} answers.  Over and over, being faced with lose-lose situations.  Cutting ties with the Undersiders versus helping Dinah.  Leaving my dad versus abandoning the people in my territory.  Leaving the city versus letting the world blow up in some unknown, undefined end of the world scenario.



And maybe I could have lived with that, could have accepted that things weren't fair and the world was biased, but I wasn't the one paying the price.  All too often, it was others around me who paid the price.  My dad had suffered for my decisions before.  And now?  \emph{This}.



Emotion was starting to creep back in.  Anger, frustration, despair, heartbreak.



I blinked rapidly, to keep my eyes as dry as possible.



The anger, of all things, was comforting.  It was something that pushed me to \emph{act}, to move, when I wanted nothing more than to give up.  I hurt everywhere, I had nobody left to rely on, and I felt drained.  The fear, the hopelessness, it was seductive.  It was urging me to give up.



The lights in the stairwell died as the bugs severed the output from the generator.  I tried to use the surprise to pull free, but Defiant and Dragon didn't even slow down.  Their grips were firm.



I gave up when the struggling became too much of a chore with the pain in my shoulders.  I still had the silk cord, if nothing else.  Escape wasn't a good option.  Offense, then.



When we stepped out of the stairwell and onto the rooftop, the light momentarily blinded me.  Defiant's vessel was a mechanized dragon painted in black and green, glossy, with gold framing the shield at the dragon's forehead, at the `wings' and shoulders.  The sleek form focused the light cast by the reddening sun at the horizon's edge.  It felt like the design had all been engineered to direct a hundred gleaming daggers of light right into my eyes.



To the people out there, barring those within a third of a mile who had been evacuated, this was a diversion.  It was little more than something to discuss at the dinner table, or watch on the late night news.  The area being evacuated, the fighting, the destruction.  Even the demise of the PRT director wouldn't have a huge impact on the average citizen of Brockton Bay.  Spotting Dragon's heavy vehicle-suit circling overhead would barely warrant twenty words in small talk.  It wasn't so noteworthy to the people down there, probably wouldn't change the course of their weeks or evenings.



To me, this was \emph{everything}.  It was the rest of my life, my friends, my father.  I'd \emph{lost} someone.  Brian or Rachel.  The only people who would fit the bag.  I was doing what I could to avoid dwelling on it, glad that I hadn't yet confirmed it either way, because it let me feel like it was Rachel when I was thinking about Brian, or vice versa.



It couldn't end like this.  I didn't want to get taken in.  I had to find a way.  My plan, as minor and feeble as it was, was easy enough to put into action, with him holding me like he was.  My bugs moved down the length of his arm, then traveled around his midsection, twice, with the cord following them.  There were only two people to tie Defiant to.  Doing it to myself would be nearly useless.  That left only Dragon.



I bound the other end around her left foot.  The slack trailed several feet behind us.  A cord as thick around as two of my fingers put together, as strong as steel.



``Before you take me in,'' I said, ``Could I have a word?''



Dragon turned to look at me, but didn't speak.



``A word with Defiant,'' I said.  ``I'm not going to try anything.  He doesn't even have to say anything.  It's sort of a last request.''



Defiant's mask opened with a barely perceptible noise.



``A last request,'' he made it a statement rather than a question.  ``We can talk in the Pendragon.  There's no need.''



``I spent the day in a cell, I wanted some fresh air.  Sue me for thinking you actually \emph{meant} something when you apologized, that you were sorry for not being fair to me back then,''  I sounded more petulant and bitter than I liked.



He glanced at Dragon, and the silence suggested there was a dialogue happening.



``It's rude to whisper,'' I said.  Again, more petty than I wanted to be.



``She can't speak out loud,'' Defiant said.  ``It's complicated to explain.  She's under certain \emph{restrictions}, many related to the PRT, and we'd agreed we didn't want to win like that, back at the school.  The only way for Dragon to stop was if I stepped in and \emph{made} her stop, and she was hurt in the process.  The recovery is slow.''



\emph{Only if he made her stop?  Because the PRT would be harsher with her, with whatever leverage they had over her? } I thought.  Was that something I could use?  What did they have on her that they didn't have on the hero-on-probation?



``Thank you,'' I said, to Dragon.  ``For doing that.''



She gave me a curt nod in response.



``I've been trying to grow as a person, with Dragon's help,'' Defiant said.  ``I'm willing to listen, but it'll have to be fast.''



``Okay,'' I said.  I glanced at Dragon.  I almost hated to do this, but I'd already started, and I couldn't go to jail.  Not with things as they stood.  ``Can I talk to him in private?''



Defiant and Dragon exchanged a look.  He nodded once, and she took flight, heading towards her airborne vehicle-suit.



The cord went taut, and Defiant's grip on my arm was wrenched away as he was dragged back.  Heavy as he was, Dragon's jet was powerful, and he wasn't on his guard.  It took him seconds to realize what was happening, to get his footing and shift his center of balance lower to the ground.



I was already moving, chasing him.  There was no point to trying to escape if they were right on my heels.



He came to a stop at the edge of the roof, but I was already arriving, taking advantage of his lack of balance to throw myself into his upper body.



\emph{Not the first time I've fought a dragon-man on a rooftop}, I thought\emph{, }as I felt Defiant move in response, all of his sturdiness and armor nothing with a strong push at the right moment.  \emph{One to mark the start of my career in costume, the other to mark the end?}



If he'd had a mind to, he could have grabbed me and taken me down with him.  Maybe Armsmaster would have.



But Defiant twisted as he tilted backwards, drawing his folded-up spear and striking out in the same motion.  It bit into the concrete of the rooftop's edge, the head expanding for a more secure grip.



I kicked the spear, as if I could dislodge it, but only succeeded in hurting my foot.



Dragon caught me a moment later, pushing me away.  She offered Defiant a hand, and he used both her grip and the spear to right himself, pulling himself back from the edge.



He stepped forward and gripped me by the front of my oversized prison-uniform t-shirt.  ``\emph{Stop that}.''



I only glared.



``\emph{Stop trying things},'' he repeated, as if he thought repetition would get through more than articulation.



``Fuck you,'' I said.  I didn't like how I sounded.  The guise of confidence I was so used to wearing was slipping away.  ``Fuck you and the people you work for.''



``I don't know why I--'' he said, then he stopped abruptly.  Was Dragon interrupting?



``You bastards,'' I said.  I could feel the veneer starting to crack.  The tears that had threatened earlier were now promising to overflow.



``You don't have any conception of what you did, do you?'' he asked.



``I have \emph{some},'' I said.  ``But no, you assholes knocked me out.  I don't know anything that's been going on.  I attacked Tagg and Alexandria--''



``They're dead,'' Defiant said.



\emph{Dead}.  I hadn't believed Alexandria would die like that.  She'd flown away.  Surely there were methods.



``A family man--''



``A bully,'' I said.  ``Twisted by the Simurgh, probably--''



``He was vetted,'' Defiant said.  ``But he's not important.  You killed one of the strongest recognized heroes in the world, at a time we needed her most.  Her image, her courage, her \emph{help}.  Do you know what's going to \emph{happen, }now?''



``I do,'' I said.  ``It's going to crush the morale of our defending forces, and it's going to break the hearts of \emph{billions} of people around the world.  I knew it when I made the call, but I did it anyways.''



``And you doomed us all.''



``\emph{She} doomed us all.  \emph{She }was the one who did it, her and Tagg.''



``Maybe.  Probably.  They forced your hand.  I understand that, and I've been trying to be lenient.  Gentle, even, though it's not familiar to me.''  His tone changed, ``You're making it hard, you keep \emph{trying} things.  Trying to kill me.''



``You would have survived,'' I said.  ``A six-story fall in armor like yours?  I could have run while Dragon looked after you.  Gotten my hands on another weapon or something.''



He didn't answer right away, but there was nothing indicating an exchange between him and Dragon.  His voice was tight with restrained anger when he said, ``You could make this easier.''



``I don't \emph{want }to make this easy,'' I said.  ``As long as you work for \emph{them}, I'm going to fight you.  You want to know what Alexandria did?  She and Tagg convinced me that the PRT is more trouble than it's worth.  If we have to rely on \emph{them} to win this, then we don't deserve to win.''



``That's a choice you just made for a whole planet of people,'' Defiant said.



``A choice I'm making for \emph{me}.  I think we can find a way past the end of the world, it can't be impossible to survive the meantime without the PRT.''



``\emph{This isn't going to work}.''



The voice was female, and it came from Dragon's direction.



``I'm having my doubts as well,'' Defiant said.



``\emph{We're low on options},'' the voice sounded.  It wasn't Dragon, but someone communicating through a speaker on her shoulder.  I recognized the voice.  Miss Militia.



``Where is she?'' I asked.



Defiant pointed at Dragon's airborne craft.



``You're not just here to arrest me?'' I asked.



``No,'' Defiant said.  ``Or we \emph{weren't}, until you decided to try to push me off a building.  Now I'm reconsidering.''



``\emph{Tell her the plan},'' Miss Militia said, through the speaker,  ``\emph{We don't have any more time, for reconsidering or anything else.}''



Time?



I glanced over my shoulder at the sun on the horizon.  It was still twenty or thirty minutes from sunset.  I must have been out for an hour or so.



But\ldots the deadline didn't matter anymore, did it?  The Undersiders should be attacking already, after being attacked, it was almost inevitable, if Grue or Rachel\ldots



I shook my head.  ``No.  No, no, no.  \emph{No.}''



``Skitter--''



Too many things that hadn't made sense.



The fact that the Undersiders hadn't gone on the offensive, or rescued me here after the PRT left me in my cell.



Alexandria keeping to her schedule, the little clues she'd given, like reminding me she could be drowned.  The baiting, the pressure, even from the moment Tagg was introduced.



Even the way she'd avoided stopping Coil, avoided stopping \emph{us}.  The way she hadn't stepped in against the Nine, or against Echidna, at first.  There had been something bigger going on.



``Why?  For what?'' I asked.  ``A ruse?  \emph{Playing} me?''



``Yes.  With one tragic mistake that we're \emph{all} about to pay for.''





