





Dragon's craft closed the distance to the rooftop's edge, using precise adjustments to almost freeze in mid-air as it hovered.  It was gentle and graceful in comparison to Defiant's squat, durable \emph{tank}.  I wondered how intentional that was.  Just looking at it, I had little doubt that it was even longer range than any of the other models I'd crossed paths with.  I was put in mind of a sniper rifle, long, narrow, sleek and focused in its almost singular design.  The stability it had fit with the idea.  A stark contrast to Defiant's craft, which seemed more like the type to be in the thick of a fight, fighting alongside him and complementing his fighting style.



Not that the aesthetics of Dragon's work was really a priority right this moment.



``A mistake,'' I said.



``We know how she operates,'' Defiant said.  ``Dragon, Miss Militia and I have each worked directly under Alexandria at some point.  It's something of an unofficial policy to have anyone that's being considered for a leadership position working under each member of the triumvirate for a time.''



``Must have been real fun for you guys when you found out what they're \emph{really} like, last month.''



``Not fun at all,'' Miss Militia said.  She had to stoop to exit the ship and step onto the roof's edge.



``We've seen how Alexandria handles interrogations,'' Defiant said.  ``She reads microexpressions.  Shapes every statement and action to get the responses she wants.''



``And she wanted \emph{this}?'' I asked.



Defiant shook his head.  ``Knowing her, this was a gambit.  It wouldn't do to have \emph{one} workable outcome.  She pushes you, and if you attack, she has cause to finish you off or send you straight to the birdcage without a trial.  If you \emph{don't} attack, she knows she has leverage against you \emph{and} the Undersiders.  She'd see which way you were leaning, then refine her approach further.''



``And here I was,'' Miss Militia mused, ``Thinking you didn't have a head for this sort of thing, Defiant.''



``I've had help,'' he said, glancing at Dragon.



``But she didn't get either of those results,'' I said.  ``At least, not like she wanted.  For all her brains, for all this apparent ability to read me, she\ldots didn't understand what my friends mean to me.''



``I think she understood well enough,'' Defiant said.  ``But the mistake, the tragedy in all of this, was that she didn't get an accurate read on you.  Much, I expect, for the same reason my lie detector could never seem to.  She was working with bad information, and she pushed you too far, too fast.''



An eerie parallel to mistakes Tattletale had made in the past.  And\emph{ I killed Alexandria and Tagg because of it.}



``And\ldots my friends?  Just to make sure.  They're okay?''



``Alexandria didn't touch them.  The ones she brought into the building were body doubles, and the \emph{real }Undersiders are poised to attack in--''  Miss Militia reached for her phone.



``Fifteen minutes,'' Defiant said.



``Fifteen minutes,'' Miss Militia said.  ``In the meantime, we're trying to deal with \emph{your} lawyer, who got his hands on the footage of the interrogation and is threatening to bring hell down on our heads--''



\emph{Earning his pay}, I thought.



She continued without pause.  ``--And we still have to find a way to handle this without a complete PR catastrophe.  Once the media gets hold of this, we lose the ability to control the situation.''



``Dragon is managing the details as we speak,'' Defiant said.  ``She can isolate and track digital communication, but she can't stop the spread of word of mouth.  Chevalier's doing what he can on his end, but the PRT agents that confirmed Alexandria's death won't be able to keep their mouths shut forever, not with something as grave as this.''



``Fifteen minutes,'' Miss Militia said.



``Fourteen,'' Defiant cut in, correcting her.



``\emph{Fourteen} minutes,'' she said, ``That's our working timeline.  Even if Skitter were to call off the Undersiders, we have information leaks.''



``Then what if we let it leak?'' I asked.  ``We say `fuck it, the PRT is fucked, Alexandria is a monster, let people figure it out for themselves.'''



``You don't really want that,'' Miss Militia said.



``The system is fucked,'' I said.  ``Everything that's happened, it's taught me a few things.  People are fucked up, for one thing.  And any organization that has people in control is going to be fucked on an \emph{exponential} level.  But for all that, people are a hell of a lot tougher than we give them credit for.  We \emph{survive}.  We innovate.  So yeah, I'm seriously thinking along those lines.  I wouldn't mind seeing the PRT \emph{burn, }damn it, because I think we'll make it regardless.''



``Why?''  Miss Militia asked.  ``What changed your mind from the moment you decided to surrender?  Your friends weren't at risk, you already knew something about Tagg and Alexandria.''



``You,'' I told her.  ``You were part of it.''



``I didn't do anything.''



``\emph{Exactly}.''



``You can't blame me for standing out of the way.  You had a plan, Alexandria told me \emph{she} had a plan, and nobody shared anything substantial with me.  I couldn't take a step without risking that I'd get in \emph{someone's} way.''



I frowned.



``You're hurt, you're angry, you're still reeling from what you \emph{thought} happened,'' Miss Militia said.  ``Fine.  That's fair.  But we don't have time to work through that.  You said you wanted to work together, to \emph{compromise}.\emph{  }Do you stand by that?  Are you willing to at least \emph{try} a workable solution?  Or are you going to keep fighting us?''



I glanced at Defiant.  ``I'll hear you out.''



``We need you to call your team and get them to stand down.  We can't have bloodshed, and we can't have Tattletale divulging critical information.''



I folded my arms.  ``Meet me halfway.''



``Twelve minutes,'' Defiant said.  ``This isn't the time to be hard-nosed.  You don't want this fight any more than we do.  If this happens, your team will be at a very \emph{real} risk of death or arrest.  Three of the A.I. models, Dragon's, mine, the Brockton Bay heroes and no less than ten \emph{visiting} heroes.''



``This is \emph{exactly} the time to be hard-nosed.  The Undersiders get left alone.  Those are my terms.  Figure it the fuck out.''



There was a pause, an exchange of looks between Defiant and Dragon.



``We're talking to Chevalier and the Chief Director,'' Defiant said.



``Good,'' I answered him.



A few seconds passed.  I glanced at the sun, dipping beneath the mountains to the west.



``\emph{Miss Militia will fill in as an interim PRT director},'' a male voice sounded from the speaker at Dragon's shoulder.  Chevalier.  ``\emph{I'll }\emph{arrange it.  We have leverage, with the current state of emergency and the issues that are liable to come up with the announcement that we can make use of the portal.}``



``And I'll remain hands off, unless I'm replaced or I have no other choice?'' Miss Militia said.



``\emph{We'll keep you in position for as long as we can, }\emph{postpone any changes or replacements until people get more comfortable with the idea.  With luck, we can segue into keeping you in position on a permanent basis. Failing that, we tap someone sympathetic to our aims.}''



``Damn it,'' Miss Militia muttered.  ``I feel like my lifespan just got cut short.  Double the work, too.''



``We'll figure out a way to make it work,'' Defiant said.  He looked at me.  ``Satisfactory?''



``Yes.  Phone?''



Miss Militia tapped out a password, then handed me hers.



I dialed Tattletale's number.



When Tattletale \emph{didn't} pick up on the first ring, I felt my heart jump into my throat.  She'd never done that.



``\emph{Lo},'' Tattletale said.  I let myself breathe a sigh of relief.  She continued, ``\emph{Call display says PRT Phone server.  Who am I talking to?}``



``It's me,'' I said.



``\emph{You!  You wouldn't believe how worried I've been.  Or}\emph{the headache I have.  You know they gave you bad info?}''



``I know,'' I said.



``\emph{The stuff you were writing, it didn't match up.  Tried to tell you, but you couldn't understand me.}''



``I know,'' I said.  ``Just tell me\ldots everyone's safe?''



``\emph{Everyone's accounted for.  Shit, what did they do?}''



``Tattletale--''



``\emph{They tried something.  What happened?''}



``Tattletale,'' I said, raising my voice a notch.  ``Time's short.  Call off the hounds, literal or otherwise.  Delay.''



``\emph{Delay}?''



``They're making temporary offers,'' I said, eyeing the heroes, ``We can make some temporary concessions.''



``\emph{Okay.  But I can't hold back some of the bastards we put into play.  I can stop them, but that's it.  They'll leave, and we're that much weaker.}''



``That's fine,'' I told her.  ``These guys are at a bit of a disadvantage too.''



``\emph{Okay\ldots let's see\ldots alright.  Holding off for\ldots half an hour?  Adding fifteen minutes to the clock?}'' Tattletale asked.



``Longer?'' I asked.



``\emph{Any longer and more mercenaries start walking away, deciding to take the half we paid up front.}''



``That'll do, then, I guess.''  I said, giving the heroes a thumbs up.



``\emph{You said}\emph{they're weaker, huh?  }\emph{So it's true.  I didn't want to use my power to verify\ldots but the rumor mill is right?  Alexandria bit it?}``



``Yes.  I--'' I stopped.



``\emph{You?  You did it?}''  Tattletale asked.  ``\emph{Guys-}''



Her voice faded as she turned away from the phone.



``Don't tell them,'' I said, once I realized what she was saying.



It was too late.  I could hear jeers and whooping from Regent and Imp in the background.  I couldn't make out everything Grue was saying, but I caught something along the lines of `\emph{Jesus H. Fucking Christ.}`



``\emph{It's too late to matter, honey bear},'' Tattletale said.  ``\emph{I don't have much juice powerwise, but I don't need any to know this much.  Word's already out about Alexandria.}''



``Word's out about Alexandria,'' I said, for the benefit of the heroes.



Defiant folded his arms.



``\emph{Anything else I can do}?'' she asked.



``Stay near a phone.  Thank you,'' I said.  \emph{And keep the jailbreak specialists on hand, }I thought.  Not that I could say that with the Protectorate members around me.



``One disaster averted,'' Miss Militia said.



``Held at bay,'' Defiant said.  ``The word's spreading.  It's starting to pop up on isolated channels.''



``We'll need to get our official word out first,'' Miss Militia said.



``What do you even say?'' I asked.  ``She's dead.''



``And that will make a lot of people lose hope,'' Miss Militia said.  ``We have other ideas, but we need something bigger, more concrete.''



``But she's \emph{dead},'' I said.  ``The only way to change the reaction is to convince everyone we have a winning game plan \emph{anyways}.  That the PRT \emph{isn't} fucked, which it is.''



``The A.I. craft,'' Defiant said, turning to look at the Pendragon.  ``Expendable, versatile, devastating in their own right, and there's \emph{image} attached to them.  They'll get the public's imagination fired up.''



Miss Militia shook her head.  ``There'll be doubts, it's not enough.  Behemoth can generate electromagnetic waves that wipe out electronics.  Even many \emph{reinforced} electronics, if he's close enough.  The Simurgh can scramble coding.  We don't just have to convince the public.  We need to convince the \emph{heroes}, and they know these things.''



``And they know what the difference is going to be, without Alexandria on the front lines,'' Defiant said.  He sighed audibly.  ``\emph{Four} times now, she's been the deciding factor in beating the Simurgh back early.  \emph{Once} with Leviathan, when I was new to the Protectorate.''



``We can reduce the impact of the loss with careful word choice and a good speech,'' Miss Militia said.  ``\emph{If} Skitter is willing to call off her \emph{other} dogs.''



I glanced at the phone in my hand.  ``Okay.''



``No demands this time?''



``Believe it or not, I \emph{want }to fix things,'' I said, as I dialed Mr. Calle's number.  ``We're on the same side here.  The difference is I consider my friends to be a part of a workable scenario.  I have my issues with you guys, but I'm extending the benefit of a doubt \emph{again}, and I'm hoping it doesn't come back to bite me in the ass.  Again.''



The phone rang.  Mr. Calle answered.  ``\emph{Quinn Calle speaking.}''



``It's Taylor Hebert.''



``\emph{Ah, excellent.  I'd feared they'd executed you or sent you to be incarcerated.}''



``I'm sorry for, um, \emph{that},'' I said.



``\emph{They had one of your good friends in a body bag, or they led you to believe they did.  You reacted as many would, with anger and pain.  You were simply, how to put it\ldots better equipped than the rest of us mere mortals to express that anger and pain.}''



``I wouldn't have blamed you if you'd left.''



``\emph{Rest assured, Ms. Hebert, I've dealt with worse.}''



``Okay,'' I said.  ``I need you to back off on whatever threats you're directing at the PRT.''



``\emph{No can do, I'm afraid.}''



``Why the hell not?''



``\emph{Because, right at this moment, you're in the custody of the heroes.  They've given you a phone, no doubt, and they've caught you at an emotionally vulnerable moment.  For your benefit, I can't assume you're of sound mind or that you aren't being coerced.}''



``How do we change your mind?''



``\emph{I wouldn't mind an invitation to the discussion.}''



``We're sending a vehicle your way,'' I said.  ``Where are you?''



``\emph{The lovely little shop with the donuts I visited this morning.}''



``Okay,'' I said, putting my hand over the mouthpiece, ``He says--''



I stopped.  The armored suit Miss Militia had left was already moving, heading directly for my territory.  She'd been listening in.



``Never mind.''



``Let's talk about our game plan,'' Miss Militia said.  ``We've got the peripheral stuff in the works.  You're bringing the suits in?''



``Yes,'' Defiant said.  ``She is.  Chevalier is on the way as well, and we've contacted the media.''



Miss Militia nodded.  ``The two major crises are being held at bay, thanks to Skitter's cooperation.  We can't keep the word from spreading through other channels, so let's cover every base we can.  We only get one shot at this.''



``Key points being Skitter's role in this, and addressing how we deal with Alexandria's demise,'' Defiant said.



``My role?'' I asked.  ``I thought you wanted me to call off the attack?''



``No,'' Miss Militia said.  ``There's more.''



I narrowed my eyes, very conscious of the fact that there were three rather powerful capes and one mechanized suit in my immediate vicinity.  ``\emph{What} more?''



She glanced at Defiant, then back to me.  ``We'd like you to be there for the conference with the media.  Dragon's going over footage, and so long as your lawyer doesn't release the unedited content, we can hide the worst of the details from the media.  Shape the narrative.''



``You're lying,'' I said.



``We're revising the truth,'' she said.  She paused.  ``Yes.  We're lying.''



``And you want me to participate in that?''



``Yes.  Your presence will lend a degree of legitimacy to what we're saying.  We're on opposite sides, in the public eye, making it all the more meaningful if we agree on what happened.''



``Are you fighting to keep the PRT going, or are you working to rebuild it?'' I asked.



``Rebuild it,'' she said.  No hesitation.



``And you're doing it by starting with a lie.  Just like they did.''



``Yes,'' she said.  Again, there was no hesitation.  ``There's no pretty, perfect answers, and concessions have to be made.  Questions and issues on a greater scale mean more repercussions for failure, and they call for bigger concessions if we want to ensure success.''



``And this is a big event, a lot of power,'' I said.  ``Big concessions?''



``Yes,'' she said.  She looked ten times as tired as she said it.



I folded my arms.  I couldn't \emph{disagree}.  I didn't like it.  But I'd been a leader.  I'd made shady calls.  I'd hurt people.  Had lied, cheated, stolen, killed.



The sun was gone, hidden by the mountains, and the clouds were changing from purple to black.  How long until the \emph{new} deadline?  Twenty minutes?



I could see Defiant, saw him conversing with Dragon and Miss Militia.



I saw how he folded his arms, still holding his spear, so it rested against his shoulder.  How he planted his feet further apart.  A warrior's stance.



It inspired a memory, of my first night out in costume.  The bad guy lying defeated on the street below, the city quiet around us, the dark sky overhead, with only meager light illuminating us.  Framing the situation, talking about options and priorities.



Not so different from the scene here.  The villain wasn't \emph{here.  }Alexandria had fallen a distance away.  But the city was quiet, the area still blockaded, the sky was dark, and the topic of discussion\ldots



I thought of something, one moment in that night's discussion when I'd thought that maybe Armsmaster could live up to the reputation, that he could really truly be someone who I could look up to.



``Hey,'' I said.



Heads turned my way.



``As far as Alexandria goes, what if we turn it around?''



``Turn it around?''



``Way back, when I first started out in costume, I had a talk with Armsmaster.  He told me that I should be \emph{happy} I was mistaken for a villain, because it meant I didn't have to fight the Undersiders.  This was before I joined them.  It reminded me of how I'd been trying to deal with the shit I was going through back then, turning negatives into positives.  I think we can do that here.''



``How?'' Miss Militia asked.  She glanced at Dragon's craft, just now arriving to bring my lawyer to us.



``So long as we're lying,'' I said, ``Let's go wholesale.  We present Alexandria as the villain she was.''



``That'll make the situation worse,'' Miss Militia said.



``It depends on how we present the idea,'' I said.



Dragon's suit once again came to a stop at the edge of the roof, as it had when it had delivered Miss Militia.  It turned sideways, and the body opened, revealing my lawyer, looking more stressed than I'd seen him, in the midst of a rather compact cockpit.



Mr. Calle accepted Miss Militia's offered hand in stepping down to the rooftop, and seemed to relax the instant his feet touched solid ground.



``Whoo,'' he said.  ``Never let it be said that my job isn't an adventure.  You're well, Ms. Hebert?''



``I am.''



``You haven't made any deals?''



``Nothing permanent.''



``Good.''



Dragon touched my shoulder.  When I turned her way, she set her fingers in my hand, pulling me after her with the light contact of two of her fingertips.  Gentle, easy to avoid, but clear enough.



I followed as she led me to her hovering Dragon-craft, Mr. Calle a step behind me.  Mr. Calle had longer legs than I did, but he was the one who hesitated at the gap before stepping into the open cockpit.



Once I was on board, Dragon reached over to the wall and opened a shallow drawer, no more than three inches deep.  The drawer opened with a noise like something from a science fiction movie.



I stared at the contents.



``How?'' I asked, and all of the confidence was gone from my voice.  ``Wait, nevermind. You're fu- you're tinkers, damn it.''



Mr. Calle stepped up beside me, placing one hand on my shoulder in an uncharacteristic need for some support.  He looked down.  ``I take it we've reached something of a consensus here?''



``I have no idea,'' I said.



``Yes,'' Defiant said, from the rooftop.



``Then it seems I need to draw up some paperwork,'' Mr. Calle said.  ``For formality's sake, if nothing else.''



``Do it in five minutes,'' Miss Militia said, from Defiant's side.  ``We're out of time.  The media's here.''



``Five?''  Mr. Calle seemed momentarily pained.  ``Paper, fast.''



Dragon handed him a sleek keyboard, pointing to a screen.  He started typing.



``I'll credit you this, Ms. Hebert,'' my lawyer said, as he typed away, tabbing to different windows to draw up pages he could copy-paste from.  ``You manage a great deal of grief and chaos in very short spans of time.''



\sectionbreak



Chevalier had arrived, and stepped into the cockpit.  Gold and silver armor, his cannonblade resting against one shoulder.  He briefly clasped hands with Defiant.



I stopped tidying my hair long enough to take the stylus from Dragon, scribbling my signature on the offered pad.  Others were already present – Miss Militia's and Defiant's.  The Chief Director's signature appeared as the document was signed from a remote location.



``You're ready?'' Chevalier asked me.



I shook my head.  ``No.''



``But you're willing?''



``Yeah,'' I said.  I rubbed my arms, then  zipped up my prison-issue sweatshirt.  ``Has to be done, doesn't it?''



``It's not pretty,'' he said.  ``There's a lot of ugliness in this.  But yes.  This gives us the best chance.''



I nodded.  I still had Miss Militia's phone.  I dialed Tattletale.



``\emph{Yo?}``



``Turn on the TV,'' I said.  ``And call them off.  Unless something goes horribly wrong, this is it.''



``You're sure?''



``Yeah,'' I said.  \emph{No}, I thought.



I hung up.



All together, we stepped out of the cockpit and walked around the craft.



The Wards were here.  Clockblocker, Vista, Kid Win and Crucible, standing on guard.



Rounding the corner, we approached the open street where the crowd of reporters waited.  Television cameras shifted to focus on the reporters announcing our arrival, or to follow us as we walked.  Tripod-mounted lights cast shafts of light across the road, all converging on one point, the makeshift stage – the flat ledge of the Dragon-suit's wing, five feet off the ground.  Voices bubbled around us, a million questions, almost a singular noise.



Chevalier stepped forward, and they simultaneously drew quiet.  He had a presence, a kind of nobility that garnered respect.



``Today, not two hours ago, Alexandria was killed.''



I could barely see the reporters past the massive lights that were shedding light on the stage, on \emph{us}.  They were solemn, focused on every single word.  They didn't even flinch at the news.  They'd already known.



``Alexandria was a veteran among capes.  She was one of the first capes, one who was present for almost every major catastrophe in the last twenty years.  With every challenge she surmounted, she reaffirmed our belief in her, showed us how strong she was, how impervious and noble she was.''



He lowered his head.  I resisted the urge to fidget.  This was showing live, to homes across America.



On a rooftop nearby, capes teleported in.  Other capes, flying, were touching down on top of a news car.  Dovetail, with Sere beside her.



``If that was it, this would be hard enough,'' he spoke.  ``But she was a mythic figure in her own way.  She was a living symbol, recognized across the world.  She was a leader among us.  She was a friend to some of us.''



I sensed rather than saw Eidolon, hovering well above the reach of the lights.  Legend was close too, though less intent on hiding.



I steeled myself for what came next, willing myself to stay calm, to not give anything away.



``And she was a traitor.''



\emph{That} garnered a response from the news reporters.  Shouted questions pierced the silence that loomed in the wake of Chevalier's words.



He continued.  ``When Alexandria was slain, earlier today, it was done by individuals standing on this stage.''



Every word carefully chosen, so it was technically or at least partially true.  Alexandria was a traitor, with her involvement with Cauldron, she \emph{had} been slain at the hands of someone on the stage.



``There are individuals out there right now, who have kept quiet about recent events.  Only last month, there was an event in this city, a threat that was theorized to be a nascent Endbringer.  In the wake of that event, Alexandria was revealed to be partially responsible.''



The reporters, I noted, were deathly still.  Deer in the headlights.



``\emph{Good} capes,'' Chevalier said, ``Burdened by conscience, walked away from the PRT.  Without them to serve as our backbone, we were left gutted.  There has been rampant speculation on what has been going on within the PRT, on what might have caused so many capes to abandon it.  We –\emph{they}– couldn't speak because Alexandria held a position of power, because she was purportedly invincible, unassailable.  Because of the threat she posed, and the resources she had at her disposal.''



Others were joining the crowd of reporters.  Civilians, returning now that the blockades had been taken down, maybe going home, only to see the scene, the heroes in the spotlight.  They clustered, or parked at the periphery of the crowd, getting out of their cars.



How many millions were tuning in right this moment?



``Some of us left, because their consciences couldn't bear serving a corrupt power.  Others, many of us on the stage included, stayed, because we felt the PRT, the Protectorate, the Wards program and the teams that draw on us for resources were too important.  I'm not here to say one decision was better than the other, or to lay blame with those who sided with her.  In coming weeks and months, our capes, accountants and lawyers will be meeting with anyone and everyone in a position of power within the Protectorate program or the PRT, ensuring nothing of this scale occurs again.''



Something moved into my range.  An insect.  Large.



Atlas.



I moved him experimentally, and felt how incredibly weary he was.  His reserves of energy were drained, his body dying.  His forelegs touched the walls around him.  He'd been placed in the back of a van.



And the occupants of that van – bugs entered open windows to make contact with the others.  Lisa, Brian, Alec and Aisha.  I could hear the echo, time delayed by five seconds, as they watched Chevalier speak on a tablet PC.



 ``Alexandria betrayed us on a fundamental level, and the whole cape community has felt that.  The\emph{ public} has felt that.  I urge people not to blame her.  She had no less than eighteen fights against the Simurgh.  We had been led to believe her powers rendered her immune, but she was clever enough to hide and alter the evidence.  She was a victim, and it's a testament to her character that she fought off the Simurgh's influence for as long as she did.''



\emph{And there's the first egregious lie}, I thought.



With luck, nobody would believe anyone that was callous enough to point it out.  Nobody would \emph{want} to believe them.  It was an ugly thought, that Alexandria could be twisted to act against our interests just because of who she was.  She'd worked with Cauldron, had experimented on humans, all in the interest of\ldots what?  Creating powers?  Selling them?



I swallowed hard.  I knew what came next.



``It was due to a concerted effort this evening that we were able to stop Alexandria before more damage could be done.''



Chevalier reached out, put a hand on my shoulder.  He drew me closer to him, until I stood in front of him and he had both hands resting on my shoulders.



``Many will recognize Taylor Hebert, revealed to be Skitter in a controversial confrontation at the school just a week ago, a confrontation Alexandria ordered.  Taylor Hebert played a crucial role in stopping Alexandria in a moment of crisis, ending the fight.''



\emph{And now half the world hates me}, I thought, staring forward.  The glare was so intense I thought my eyes might start crossing.  \emph{And the other half\ldots I don't know what the other half thinks.}



I'd agreed to share `credit' for the kill, but only because there had been a consensus that people wouldn't believe it if I took sole responsibility.



Chevalier wasn't speaking.  I saw a red light go on at the corner of my collar.  The microphone Dragon had clipped there was live.  The signals would be received by all equipped, official cameras.  Something the PRT had arranged for convenience's sake some time ago.



I had a chance to speak in my own defense, in front of countless tens or hundreds of millions of eyes, and the words were dying in my throat.



My thoughts were grinding to a standstill.  What was I supposed to say?  We'd barely had any time to prepare.  We \emph{hadn't} had time to prepare.



There were whole lines I was supposed to give.  Ideas I was supposed to express, striking the right tone, and I'd gone blank.



I couldn't defend myself like this, even with rehearsed lines.



Chevalier rescued me.  He spoke, his voice clear.  ``This isn't a happy day.''



It was a reminder of what my line was supposed to be.  \emph{I'm not proud, I'm not happy that it came to this\ldots}



``It's not a happy day, but it's a \emph{good} day,'' he said, skipping ahead two or so minutes.  ``It marks change, and it marks a step forward.  A chance to fight Endbringers and other threats without sabotage, without worrying who stands beside us, or whether our leadership is compromised.''



Dragon's ships descended from the sky above.  My hair and the hood of my sweatshirt flapped as the vessels landed to either side of us.  Eleven vessels.  The ones we'd destroyed had been rebuilt, updated.  Others, old Dragon suits, had apparently been set up with A.I. to fly on their own.  They gleamed, various shades of chrome and gunmetal, with trim in different metals and colors for decoration and highlighting.



\emph{She had more made}, I thought.



``A chance to fight Endbringers without as many casualties,'' Chevalier said.  ``And \emph{hope}.  We've investigated the portal to another world, and confirmed that there are resources and even shelter, a possibility of escape in a time of emergency.''



I stared at the van where the Undersiders were.



``And new allies, as unlikely as they might be.''



His hands dropped from my shoulders.



I reached up to the zipper of my sweatshirt.  I pulled it down, then shrugged out of it.  Chevalier took the piece of clothing in one hand.



I bent over and stepped out of the loose-fitting prison sweats as well.



Defiant handed me my new mask, and I pulled it on.  Electric blue lenses, the opposite of the yellow I'd worn before.  They helped with the glare, though they weren't so good against it as my old lenses.



Light gray fabric where I'd had black.  Armor panels in the same dark gray as before, albeit with cleaner lines, less bulk, and less in the way of edges.  I had no points at the tips of my gloves, and both the mantle around my shoulders and the cloth that hung around my belt were marked with an electric blue border, with my gang emblem in miniature at each corner, flipped upside down so they faced skyward, altered to match my new color scheme.



``I admitted to reprehensible things,'' I said.  ``I won't challenge that, or pretend I didn't say or do those things.  By all rights, I should go to jail.  I may serve a sentence, if the courts will it.  I won't challenge that.''



I paused.  For a terrifying moment, I thought I'd forget what to say again.  Then I fixed my eyes on the windshield of the van, at the far end of the crowd.



It struck me that I hadn't suffered stage fright.  It had been something else entirely.  I hadn't \emph{wanted} to speak, because there would be no going back.



When I finally spoke, I didn't follow the cues I'd been given.  My eyes didn't leave the spot where the Undersiders were watching from.



``I seized a territory in Brockton Bay.  I led the local villains, and we defeated all comers.  I was secure in my position.  I had wealth, friendship, love and respect.  People depended on me.  It was everything I'd ever wanted, if not quite the way I'd initially imagined it.  I could have stayed and been comfortable.



``Except there are bigger things.  More important things.''



The eyes and cameras on me made me feel like I was deep in the ocean, a crushing weight pressing down on me.



``I believe in the idea of a new PRT that Chevalier is talking about.  I believe in it enough that I was willing to turn myself in and take action to bring it to fruition.  That I was willing to leave everything I had behind.  If I have to serve time in jail first, then so be it.  If I face the Birdcage\ldots I hope I don't.  But at least I could tell myself that seeing the supervillain step up might convince others to come back.  Change the minds of heroes who gave up on the PRT for one reason or another.''



A lump welled in my throat.  I knew I didn't have many more words left before I wouldn't be able to speak.



``This is what I want to do, above all else,'' I said, and I said it to the Undersiders.  ``Given the chance, I'll serve the people.  As I fought Leviathan, the Slaughterhouse Nine and other evils, I'll fight to the last gasp to protect all of you.  When-``



A howling in the distance interrupted me.



Moments later, others took up the cry.  Ten dogs, then twenty.  Others took up the cry around the city, from various shelters and homes.  A hundred, two hundred dogs, and the wolf cub that had started them off.



``--When and if I do take up the job,'' I finished, speaking around the growing lump in my throat, ``You can call me Weaver.''



Chevalier set a hand on my shoulder.



``That'll be all,'' the hero said.  ``We'll have another statement and a conference to answer questions early tomorrow, when we know more for sure.''



The reporters were already calling out questions.  Is this the first time you've recruited a villain?  How did Alexandria die?  What crimes did she commit, exactly?



More questions, until it was a jumble.



He led me away, one hand steady and firm on my shoulder, and Miss Militia, Defiant, Dragon and my lawyer fell into step behind us.



I cast one last glance at the van, then entered Dragon's ship.



``You stumbled,'' Defiant said.  ``Improvised.  But that was good.''



I didn't respond.



``You know you can't stay here.  There's a conflict of-``



Dragon reached out and pressed an index finger against the `mouth' of his mask.



Then she folded her arms around me.  She was cold to the touch, hard and unyielding, but she still managed a motherly embrace.



My face pressed against her shoulder, I found myself glad that my mask hid my face from view.





