``\ldots\emph{you can call me Weaver}.''



The broadcast ended.   A hush took hold of everyone present, a silence that deepened when someone muted the television.



The spell was broken by one of the kids.  Ephraim.  ``She's going to be a hero?''



``She's going to try,'' Forrest answered.



Charlotte looked around at the collected residents of the Boardwalk.  It was customary, now, to have a block party every third night of the week.  A mass-barbecue, a bonfire on the beach, or some other big meal that would bring everyone together.  Community.



\emph{Skitter's} community, though Skitter was gone, in more senses than one.



Taylor had turned herself in, early in the day, and word had spread.  They'd hooked up a television, the biggest they could get their hands on, and set it up beneath a waterproof tent for good measure.



For the better part of the day, they'd watched.  People had stopped by, glancing at the latest news.  Any update, however large or small, was met by shouted alerts, by hollers and speculation.



Charlotte had taken the day off school, taking only the time necessary to see the little ones off and to bring them back.  She wouldn't have been able to focus, anyways, and the schools were still being lenient.



And now, finally, \emph{this}.



``It's done,'' Charlotte said.  ``For better or worse.''



``For better,'' Forrest said.



``I'm not so sure,'' Charlotte said, lowering her voice so others wouldn't hear.



``She's a hero,'' Forrest said.  ``This is where she's supposed to be.''



``Maybe,'' Charlotte answered.  She couldn't help but think of how scary Taylor had been when she'd dealt with the ABB thugs.  How \emph{easily} the girl had slipped into her role as a leader of the territory.  ``But even if it's where she's meant to go, they won't necessarily accept her.''



``Doesn't matter,'' Forrest said.  ``It's out of our hands.  We'll wish her the best, give her some moral support if they let her get fan letters, and handle our own business, so she doesn't have to worry about us.  And speaking of handling our own business\ldots''



Forrest directed a pointed look at the kids who were sitting around Charlotte.



``Right,'' she said.



``I'll be along to see to the lads,'' Forrest said.  ``Just have to clean up first.''



Charlotte nodded.  Bed time for the littlest ones.  She rose from the bench.  ``Show's over, come on, it's time to go to bed.''



There were groans and grumbles here and there.  Charlotte knew who it was without looking.  She identified Mason, set a hand on top of his head, and pulled him closer to her as she walked back to their place.  ``Be good.''



Mason mimicked the exact same groan he'd given a moment ago.



``So dumb,'' Kathy was saying.  She was one of the older children, looking after Jessie and Aidan.  ``I never had to go to bed this early before.''



``It's easier,'' Charlotte said.  ``And we can \emph{all} use an earlier bedtime.  It leaves us in better shape to face tomorrow, don't you think?''



``I wasn't talking to you,'' Kathy said.



Kathy and Mason were the most likely to fight, to challenge her.  When she was hurrying to get them out to the bus stop for school, it was Mason who would decide he'd suddenly forgotten how to tie his shoes, or who would drag his feet to force her to seize his hand and pull him along.  He needed that attention in moments of crisis, however small.  Kathy was the opposite.  Charlotte hadn't uncovered the details, but the girl had been burned by someone in authority, and rebelled against it as a matter of habit.  Kathy wanted to be independent, but she was too young.



``You were complaining about something I said.''



Kathy glared at her.  ``I could stay up, watch TV for another hour or two, and then go to bed.  I'd be quiet.''



``And what if you were too tired to look after Aidan and Jessie?''



Kathy scowled, but she didn't reply.



Jessie wet the bed most nights.  She never came to Charlotte to let her know.  More than once, Charlotte had found the girl sleeping on the floor when morning came.  Aidan had nightmares that left him screaming and wailing well after he'd woken up, refusing to listen to her.  More than once, he'd actually had the nightmares while sleepwalking.



It was hard to deal with, frankly.  She'd taken to setting her alarm for one, three and five o'clock in the morning, rising from bed and checking in to make sure the kids were alright, that Jessie's bed was dry.  It was embarrassing to admit, but there had been four occasions when she'd been \emph{terrified} as she had run into Aidan, standing in the bathroom or sitting at the table in the kitchen.  Each time, he'd been gripped by whatever terrors it was that found him at nighttime.  Half the time he fought her, the other half the time he just screamed, bloodcurdling.



Kathy, a little more than half Charlotte's age, took it in stride, almost \emph{thrived} on looking after the younger ones.  She had endless patience with Jessie's nighttime accidents, and virtually every time Aidan's screams woke her, Kathy was already at his side, speaking calmly, waiting until he'd relaxed enough that she could hug and cuddle him.



They made their way inside, and Charlotte was sure to close the shutter just beyond the front door.  Aidan watched carefully as she fed the chain through the ring at the base of the door and the small gap in the floor.  She locked it, then tugged it for good measure, demonstrating how secure it was.



``Safe,'' she said.



Wordless, his forehead creased with the sort of worry he shouldn't have for another fifteen years, Aidan turned and walked away.



``Girls in the bath first, snacks after,'' Charlotte said.  ``Boys, cookies and milk before your bath.''



The O'Daly clan had collected their kids, most of their kids, finally.  It left the number more manageable.  Kathy, Mai and Jessie made their way to the bathroom.  Aidan, Ephraim, Ethan and Mason found stools at the kitchen counter while Ben, the oldest of the boys, got the cookies, glasses and milk out.



Charlotte checked on the girls to make sure that they were getting along okay, then shut the bathroom door and got her laptop out.



Welcome to the Parahumans Online message boards.You are currently logged in, \underline{Char}You are viewing:
$\cdot$  Threads on Subscribed Boards
$\cdot$  Last 12
$\cdot$  Topics only



\blacklozenge  \strong{Stickied Topic:}\strong{Alexandria Discussion (July 14th)}\strong{Goes Here}
\blacklozenge  \strong{Topic}:  \strong{Alexandria Dead}
\blacklozenge  \strong{Topic}:  chevalier's `new PRT' vs. endbringer
\blacklozenge  \strong{Topic}:  What the fuck happened?\blacklozenge  \strong{Topic}:\strong{  }Skitter
\blacklozenge  Topic:  The Endbringers, Thread XXXIV
\blacklozenge  Topic:  Dragon Suits: Continued Escalation of Cape Militarization?
\blacklozenge  Topic:  Weaver
\blacklozenge  Topic:  Undersiders
\blacklozenge  Topic:  Alexandria died
\blacklozenge  Topic:  Issues with recruiting villains
\blacklozenge  Topic:  Portal confirmed ok by Chev 2011-07-14



``She's famous,'' Charlotte said aloud.



``Because she was on TV?'' this from Aidan.



``Because she was a bad guy, and she turned around and decided to be good,'' Charlotte said.  ``And because she helped beat Alexandria.  It's controversial stuff, and I think people are going to be arguing about it for a long time.''



``She's not a bad guy,'' Ben said, taking a seat beside the other boys.



``Was too,'' Ephraim said.



``She was scary and mean,'' Ben said, ``But she's not bad.''



``They're the same thing.''



``It doesn't matter,'' Charlotte says.



``She got us pizza,'' Ben said.  ``That's all that matters to me.''



``That's sound enough reasoning,'' Charlotte said, smiling a little.



She left the laptop to visit the bathroom, calling through the door.  ``Five minutes, then out!''



She could hear another grumble from Kathy.



They'd do better if left to their own devices.  Kathy would be happier with something to do, even if it was washing the hair of the younger girls and ensuring they brushed their teeth.



She returned to the kitchen, collecting the plates and glasses and putting them in the dishwasher.



A car horn outside caught her attention.  It wasn't easy to get cars in and out of the area, with the streets still under repair, and the vehicles that \emph{were} around were construction vehicles, which didn't work this late at night.



The horn sounded again, and there were shouts in response.



She was still staring at the door, straining to make out something telling, when Ethan approached her.



``Do you need me to run an errand?''



``No, Ethan.  Now might not be a good time.''  There was more noise outside.  Voices.



``Okay,'' he said.  He looked disappointed.



``If you want some fresh air, I can let you upstairs.  You can sit on the balcony.''



Ethan frowned.  ``No.  No thanks.''



``Just give me five minutes,'' she said.  ``Ben?  Lock the shutter after me.  I'll come through the door downstairs when I return.  Let Kathy and the girls know I'll be back.''



Ben nodded.



She didn't raise the shutter all the way, stooping beneath and holding it partially closed.  Ben wasn't strong enough to lower it on his own, and the outside didn't have any real handholds.



With Ben's help, she still managed to press her hands against the broad strip of metal and push it to ground level.  There was a sound of the chain rattling through the gaps.



People were active, gathering in clusters and crowds.  The focus of attention?  A news van.



The news crew was surrounded.



``\ldots{}word out,'' the reporter was saying.  ``People are going to make a lot of ugly assumptions.''



``Just go!'' someone shouted.



``Turn the camera off and leave!''



The reporter, a tall, blond man with a broad jaw, only smiled.  ``I'd almost think you guys had something to hide.''



``We want to be left alone,'' Charlotte said.



``Not going to happen,'' the reporter said.  ``This is blowing up.  People are going to want to investigate every last scrap of dirt.  Even if I left, others would come.''



``We'll tell them the same thing we told you,'' she said.  She saw Forrest approaching, making his way through the crowd.  ``That we had school and work all day, that everyone here is working on rebuilding, and we're \emph{tired}, we're not interested in the scandal of the moment.''



``Working hard?'' the reporter asked.  ``What if I offered, say, two hundred bucks, to whoever gave me the most information?''



``We'd tell you to fuck off,'' Forrest cut in, before anyone could take the deal.



``World wants to know.  What is she \emph{really} like?''  The reporter asked.  ``Two hundred dollars, your face on camera.  If you love her, don't you want people across America to hear something good?  Best support you can give.  If you hated her, well, the opposite's true, isn't it?''



``You'd twist our words around,'' Forrest said.  ``Edit it to take the choicest bits.''



``That'd be dishonest.  It's not the way we work at channel twelve.''



``No,'' Forrest said.  ``I think that you're primarily interested in what gets viewers and ratings.  Maybe you'd stick around for two hours, interview everyone you could, and then take the most controversial and extreme statements.  Only way we don't play into your hands is if \emph{nobody opens their mouth}.''



He raised his voice a little at that final statement.



``That so?'' the reporter asked.  ``Three hundred dollars.  That's, what, two or three days' pay, with the kind of wage you earn here?''



Forrest didn't respond.



``Okay,'' the reporter said.  ``Well, there's nothing stopping us from sitting around, is there?  And if someone decides that they'd like to earn a little cash\ldots''



``They'd have to be pretty stupid,'' Forrest said.  ``Property values are set to soar here, and the way things are organized, just about everyone here is slated to earn a property or a share of a property somewhere down the road.''



``And you're saying that has \emph{nothing} to do with the fact that you all worked for a supervillain.''



``I'm not saying anything one way or the other,'' Forrest said.  ``Except that the numbers don't add up.  Three hundred dollars now, or get a share of a place that could be worth millions, a few years down the road?''



``People are enterprising,'' the reporter said.  He smiled.  ``And I can be discreet.  The public needs to know who's protecting them.''



He turned, returning to the passenger side door of the van, then paused.  ``We'll be parked on the beach.  We can blur out your faces if we need to.''



It took them a minute to get their camera packed away and leave.  Sure enough, they made their way to the beach.  Charlotte could see the headlights illuminating the sand.  Then they went out, and the van was effectively invisible.



``Guards,'' Forrest said.  ``Take shifts.  We're not giving them anything.''



``You're wanting to protect Skitter?'' someone asked, from the crowd.



``I worked for her,'' Forrest said.  ``Most of you know that.  In a way, I still think I work for her, even if she isn't here anymore.  A lot of us owe her.''



``She brought us as much trouble as she stopped,'' the person said.  Charlotte could see it was a tall man who'd hidden a receding hairline and bald spot by shaving his head.  There was only stubble, now.



``She made it possible to rebuild, Scott.''



``\emph{Everyone's }rebuilding.  We got a head start, that's all.  You're saying that's worth it?  Mannequin came here because of \emph{her}.  Burnscar came here because of her.  Or didn't you hear?''



Forrest folded his arms.



Scott said, ``My sister-in-law works for the PRT.  Wears a uniform.  She said the Slaughterhouse Nine were here because they were \emph{recruiting}.  They picked a bunch of people across the city, trying to recruit them, and Skitter was one.  Obviously.  So it's \emph{her} fault the people died here.  The help she gave?  She was probably guilty.''



``We don't know that for sure,'' Forrest said.



``Bullshit.  You were there, that first time, when Mannequin was in the warehouse on Shell.  He was wagging his finger at her.  Why?  He was there for her.''



``I was there,'' Forrest said.  ``Remember?  I stepped up.  I dragged that bastard to where we could tie his head up.  I smashed his head with a concrete block.''



``And I won't deny that,'' Scott answered.  ``I would've been right there with you if I didn't have my wife and kid to protect.  We both saw how it played out.  Going by what my sister-in-law said, you wouldn't have had to do that if Skitter had been somewhere else.''



``I would have,'' Forrest said.  ``I know Skitter.  Taylor.  Weaver.  Whatever you call her.  We've talked, talked a \emph{lot}.  I've heard her side of things, and I know you're off base.''



``You're saying my family's lying?''  Scott asked, raising his voice a touch.  ``Or maybe you're \emph{blind}.  Can't see what's going on because of your own basic, underlying \emph{bias}.''



Scott approached, moving through the crowd.  He was clearly irritated, a big guy, undoubtedly a dock worker, breathing just a little harder than normal.  Charlotte found herself biting her lip and backing away as he drew closer.  Her stomach twisted as he passed her, as though it were a towel someone was wringing out.  Not an unfamiliar sensation.



For a moment, she could imagine him in her face, hooting, hollering, a vein standing out on his bald head.



The wrenching got worse at the idea, until it felt like everything below her shoulders was being crushed.



The crowd around her was too much, now.  Too evocative.



She fled, pushing her way through the crowd.  For every part of her that wanted to follow the discussion, there was another part that could hear the discordant music blaring, could hear the yelling, smell the sweat, the smoke and incense.



She'd seen what people were like when everything else was stripped away.  Not everyone, not always, but often enough.  It was \emph{easy} to descend to that level.  Taylor had offered security.  Strength, and the ruthlessness necessary to cut out the cancer.



It wasn't rational to think this way.  Charlotte knew, generally speaking, that the people here were good.  The bad ones had been scared off, or cut out of the deals that kept everyone else loyal.



On a less rational level?  She hated the idea that this place could devolve into \emph{that}.  Into what the Merchants had become.



She was upset, she wasn't thinking straight, and she couldn't afford to return to the kids like this.  Ben and Kathy would look after the littlest ones for five more minutes.  She could keep walking, burn off this nervous energy and get in a better headsp-



``Miss?''



She jumped, swiftly backing away.



It was a man.  Thin, with glasses, reaching out-



\emph{Groping, greedy for a handful of flesh}.



No.  To get her attention.  Nothing more.  His hand dropped to his side.



``Are you a reporter?''



``I- do I \emph{look }like a reporter?'' he looked anxious, and the expression was unrelated to his question.



``No,'' she said.



``I was asking around, for someone who knew Taylor.  Someone told me to look for a girl about your height, with long, dark hair, like yours, with kids around her.  I was going to ask some more, but then the crowd came, and I decided to hang back.''



\emph{So he is here to ask questions}.  \emph{But he said Taylor instead of Skitter}.  ``You \emph{really} aren't a reporter?''



``If you know who they were talking about, maybe you could point me in the right direction?''



Charlotte frowned.  ``They were talking about me.  What do you want?''



``I'm her father.  Danny.''



\emph{Oh}.  She could see the resemblance, now that she knew to look for it.  Both he and Taylor were above average height, both were narrow.  She must have gotten her hair and mouth from her mom, though.



``Okay,'' she said.  She forced herself to relax a touch.  \emph{He's safe.  Mostly}.  ``O--''  She exhaled as she spoke, and her breath caught.  She was still a little out of sorts.



``Are you okay?''



She shook her head.  ``Yes.''



``You're sure.''



``A lot to deal with, all at once.''



``Yes.''



She glanced up at him, saw how troubled he looked.  ``Do you drink tea?''



``Coffee.''



``We can do coffee,'' she said.  She reached into her back pocket for her phone.  ``Stand still.''



He looked confused as she turned the phone his way.  The flash went off.



``What's going on?'' he asked.



``Protocols,'' she said.



``Protocols?''



She typed out a text and sent the text, picture included, to Tattletale.



``I worked for her.''



``Oh.  \emph{Oh.}''



``Come on.  We'll, um, we'll hear soon, if you're okay to come inside.  But I have to head back that way anyways.''



He nodded.



``Why aren't you with her?''  She asked, as they started walking.



``Things turned ugly.''



``Oh.  Alexandria?''



``I only just found out about Alexandria.  Maybe I shouldn't say, but things don't seem to add up.  What people were saying before, what happened, and what seems to have happened after.''



``Yeah,'' she said, though she didn't quite understand.



``All the way through this, I told myself I'd trust her.  That she was the same child my wife and I raised for the last sixteen years.  That things were muddled, but she was the same person deep down inside.''



``Isn't she?''



``I'm not so sure anymore.''



The phone vibrated.  Charlotte checked.



Tt:
A-ok.  Treat him well.



``You're clear to come inside,'' Charlotte said.  She used her hand to indicate a change of direction, leading him towards the beach.



``All this secrecy?  It's necessary?  I thought she left.''



``We still have enemies.  People who'd hurt her by hurting us.  We have to stay safe.''



He fell silent.



``What?''



``I haven't really been thinking along those lines.  About the greater scale of things, my life being at risk because I'm connected to her.''



``You learn,'' Charlotte said.  ``You learn to think that way.''



``Why?  I mean.  I don't have a choice, but you- you could walk away from this, and you haven't.''



``I can't walk away from this,'' Charlotte said.  ``I'm probably more tied up in this than you are.''



``How's that?''



She glanced down the beach.  The people who were watching out for those who might talk to the reporter were far enough away.  Still, it would be a bad idea to use her flashlight.  She reached into her pocket and pulled out a glove, pulling it on.  ``You'll see in a minute.  Hold my hand and don't let go.  Neither of us want you to get turned around in here.  Not much room to get lost, but yeah.''



She could barely see him in the gloom.  There were no lights on the beach.  Still, when she reached out for his hand, he took it, holding tight.



Carefully, Charlotte led Taylor's father into the storm drain.  Her gloved hand traced the wall.  First right.  Skip the next right, with a few seconds of nerve-wracking isolation in the darkness, then follow the wall\ldots one right, turn left at the t-junction.



They ascended to the cellar, first, and then up to the living room.



``It's a house?'' he asked.  He looked even more bewildered than before as he took in the particulars, the living room, with young girls clustered on one couch, boys on the other couch and the floor, the appliances, the stacks of boxed-up food that had yet to be unpacked.  ``Children?''



``Orphans,'' Charlotte said, keeping her voice low.  Both Mai and Ephraim could break down in tears at the slightest reminder of their departed parents.  ``I've been looking after them.''



``You can't do that.  Not like this, without certification, others checking in.''



``I know,'' she said.  ``It's only for a little while longer.''



``\emph{This} is why you can't leave?''



``Part of it.  There's more.''



``This is what she was doing, all that time?  Taking care of these children?''



``That was only a small part of it.  She mostly paid me to look after them and make sure people got the food they needed.  She looked after \emph{everyone}.  When they were all in the worst situations they'd ever faced, struggling for food, worrying every hour if they would be attacked or preyed on, she stepped up.''



``You're trying to defend her.  To justify what she did.''



``Only a little.''



Ethan approached.  He gave Taylor's dad a curious look.



``It's Taylor's daddy,'' Charlotte explained.



``Danny,'' Danny said.



``Oh,'' Ethan said.  He looked down at the floor.



``Do you want to run an errand for me?''  Charlotte asked.



Ethan nodded, still not making eye contact.  Charlotte could see how he'd set his jaw, so stern for a little man.



``Go tell Forrest that Skitter's daddy is here.  And if anyone approaches you to ask you questions, you don't answer, okay?  No matter how nice they seem, don't say a word, and blow your whistle.  There are reporters out there we don't want to talk to.''



Ethan nodded.



``Don't take too long,'' \emph{she} warned.



The little boy, no older than eight, ran off, opening the front door and unchaining the shutter.  A moment later, he was gone into the night.



``Is that okay?'' Danny asked.  ``A little boy going out alone after dark?''



``The area's safe, the people know each other.  It's a community, and the community will look after the kids.  Besides, he's got a whistle in case he gets in trouble.''



``It almost looked like he was \emph{asking} for an errand.''



``He was.''



Danny gave her a curious look.



Charlotte walked around the kitchen counter to get into the kitchen, starting the water boiling for the coffee.  She still had a habit of keeping the kettle full for Taylor.  ``Ethan's bottling up a lot of hurt, but he's convinced himself that big boys shouldn't cry, and nothing will convince him otherwise.  For now, I'll let him take five to twenty minutes longer than he should when I tell him to go do something, and I won't say a word if he comes back with red eyes and a runny nose.  If he needs to find a quiet place to cry on his own, that's okay.''



``There has to be a better way to handle it,'' Danny said.  His eyes were still roving, as if trying to find and identify Taylor's signature touches on the surroundings.



``There probably is.  But for now, it works for him and it works for me.  The other kids--'' she lowered her voice a fraction, ``They all have their individual needs.  Some get aggressive.  Some internalize it, have nightmares or wet the bed.  Others withdraw.''



Danny sighed.  ``Kids are hard, aren't they?''



``Yeah,'' Charlotte said.  Then she changed her mind.  ``No.''



``No?''



``\emph{People} are hard to deal with.''



``Maybe you're right,'' he said.



``You should really be with her.''



``I was there,'' Danny said.  ``I told myself I'd stand by her, and then\ldots all at once, it wasn't \emph{her}.  I've seen her in a crisis, after her mom died.  She was one of the people who withdrew.  When she was bullied at school, she withdrew.  But there?  At the PRT headquarters?  That wasn't her.''



``It was,'' Charlotte said.  ``Maybe you lost sight of who she was becoming, somewhere down the line.  I don't think anyone would fault you, with the secrets she was keeping.''



``No,'' Danny said.  ``I don't think it was her, not really.  For just a minute, she became a monster.''



``We all have a monster somewhere inside us,'' Charlotte said.  ``Like I was saying about the kids.  Sometimes it's aggressive, sometimes it finds other forms of attack, and other times it's a cowardly one.''



\emph{Like mine}.



Danny sighed.



``You don't agree?  I'm still off target?''



``I don't know.  I think maybe you're right.  I've got my own demons.  But\ldots whatever monster that was, it was a big one.''



Charlotte didn't have an answer to that.



There was a knock on the shutter.  Then it raised a fraction.  Forrest stepped inside, growled and made threatening gestures as the kids practically leaped off of the couches and swarmed him.



He gave Danny a funny look.



``Taylor's dad,'' Charlotte said.



``Nice to meet you,'' Forrest said.  He waded through the cluster of kids and, straight-legged, he leaned over the kitchen counter to shake Danny's hand.  ``Right, rugrats!  If you stand up to pee, get yourselves into the bath, pronto!''



``I can pee standing up!'' Mai said.  ``A girl at school showed me how.''



``Then\ldots if you think action figures are better than dolls!''



``I think army men are better than dolls!'' Mai said.



``Then let's go with those who'd rather be a baseball player than a princess!''



``I--''  Mai stopped short, shrieking as Forrest swept her up in his arms.



``I get the point,'' he said.  ``As penance, I'm letting you ride on my shoulders.''



Mai squealed in glee.



``With a blindfold, in case the menfolk are bashful.  Move along, tykes.''



Ben, Ephraim and Aidan made their way into the bathroom, followed by Forrest, with Mai sitting on his shoulders.  Forrest practically had to get on his knees to get through the doorway without hitting Mai's head on the doorframe.  The door shut behind him.



``Coffee will be done in a few minutes,'' Charlotte said, making sure things were set up.  She moved to the living room, and beckoned for Kathy to come closer.  Kathy scowled but obeyed, sitting beside Charlotte as Charlotte set to brushing out her hair.



``I couldn't recognize my own daughter,'' Danny said.  ``Every step of the way, I've wanted to help her, but I didn't know how.  Did she say anything?  About me?''



``No,'' Charlotte said.  She could see Danny's face fall.



``But,'' she said.  ``She \emph{acted} on it.  When it came down to it, she wanted to spend time with you, even if it meant that all the rest of this was harder.''



``When it came down to it,'' he said, ``She chose her friends over me.  She chose to fight, to go all out, instead of making a concession and possibly coming home at some point.''



``Bigger things,'' Charlotte said.  ``I- the rest of us\emph{ }feel a little betrayed too, but we're little more than specks, with the sheer scale of the stuff she's focused on.''



Danny sighed.  ``I came here to make a decision.  To work up some courage.  But I feel as conflicted as ever.  Worse, if anything.''



``A decision?''



``Taylor has to join the Wards, if she's going to join an official team.  Her lawyer got in contact with me, to let me know that there's certain procedures.  She needs a parent, guardian, notary, or a person in authority to vouch for her, and it has to be someone who's otherwise free of connections to superheroes or supervillains, someone that knows her and can testify about her character.''



``Do it.''



``I'm wondering if I should.''



Charlotte gave him a hard look.  He took it without flinching.



``My number one instinct is to keep my daughter safe.  If she went to juvenile detention, it would\ldots it wouldn't be good, but it'd keep her out of the line of fire.  It'd stop her from going down this reckless path.''



``She'd hate you,'' Charlotte said.  ``She'd still love you, but she'd be angry.''



``She would be \emph{safe},'' he said.



Charlotte didn't have much to say in response to that.  She turned her attention to the girls, instead.  ``Five more minutes of cartoons, then bed.  I'll fix your hair in just a second, okay, Jessie?''



Jessie nodded.



``I could, if it would make it easier,'' Danny offered.



Charlotte felt that twang of alarm at the notion of a relative stranger touching `her' kids.  She could rationalize that this was Taylor's dad, but\ldots



Jessie made the decision for her.  Standing and approaching Danny, before sitting beside him.  Charlotte tossed the man a hairbrush.



For long minutes, they worked on combing through knots and tangles.  Kathy made sure to grunt with every one.



The boys exited the bathroom, each with a towel wrapped around them, while Forrest carried a squealing, giggling Mai under one arm, a sock tied over her eyes, her hair now dry and combed straight..



``You're better than Char,'' Jessie said, as Danny finished.  She hopped down from the armrest of the chair, before scampering off to the bedroom.



``Traitor,'' Charlotte muttered, after Jessie was gone.  Kathy followed the girl, taking Jessie's hand after catching up.



There was a pause.



``If she needs you, you should help her,'' Charlotte said.



``I'm just not sure what helping her entails,'' Danny replied.



Charlotte rose to pour the coffee.  Her phone glowed with a fresh text.  She stared down at it.



``Shit,'' she said.



``What?'' Danny asked.



``Company,'' she answered.



``Enemies?  Danger?''



``Worse.  Allies,'' Sierra said, from the doorway.



Charlotte turned to see her friend, Sierra.  The girl still had her red hair bound in dreads, but the rest of her was all professional attire.  Nice shoes, slacks, a blue dress shirt, and just a little makeup.



Sierra approached, arms reaching out to hug Charlotte.  Charlotte welcomed the hug, murmuring the words, ``I missed you.''



But her eyes were still on the doorway.  Tattletale stepped into the front hallway, followed by Grue and the pairings of Imp and Regent, Parian and Flechette.



\emph{A superhero, here?}



After a brief pause, Bitch entered as well, glowering, looking fit to murder something or someone.  Her appearance was at stark odds with the puppies that followed her, each at the end of a differently colored leash.



Danny stood, eyes widening as he recognized the people entering the room.



``Long time no see, Danny,'' Tattletale said.



``Lisa,'' he answered.  There was no warmth in his tone.



``Tattletale while I''m in costume, please,'' she said.  She flashed a grin, and he didn't return it.



Grue extended a hand to Danny.  It took the man a second to accept it.  He watched the group warily.



``What's going on?'' Charlotte asked.



``Need to watch your phone,'' Tattletale said.  ``I sent you a string of texts.''



``I was busy.  Looking after the kids, and talking with Danny.''



``Right,'' Tattletale said.  She made her way to one couch, then lay down.  ``Damn.  Hell of a day.  Not enough sleep, already feeling like shit, and then \emph{this} gets dropped on us.''



``What's going on?'' Charlotte asked, again.



``You mean what's going on \emph{here} or what's going on in general?  \emph{Generally}, our commander-in-chief just defected to the white hats.''



``Here,'' Charlotte said.  ``Why are you here?  We're just getting the kids off to bed.''



``Loose ends,'' Tattletale said.  ``A few here, a few there.  Skitter's gone, and she's liable to spend time in prison before she joins the Wards, and she won't be able to visit for a while, even after that.  I want to get this as done as we can, so I can sleep for a few days straight and wake up feeling better.''



Charlotte frowned.  Tattletale had taken up one couch, Grue was sitting in another, and she didn't want to sit next to him.  She was forced to stand, but standing and being a part of the conversation meant standing in a place where her back was to Bitch, to Parian and Flechette, who were sitting on stools by the kitchen counter, and to Regent and Imp, who were rifling through cabinets and drawers, in search of snacks.



``I have to ask.  Why the puppies?'' Charlotte asked, glancing at Bitch.



``Tattletale said to.''



``That's not exactly right,'' Tattletale said.



``It's what you said,'' Bitch responded, sounding irritated.



``I recommended puppy therapy,'' Tattletale said.  ``Everyone loves puppies, so maybe it's a way to deal when we're feeling a bit lonely?''



Bitch looked at Charlotte.  ``You miss her?''



``Um.  Yes?''



Bitch bent down, grabbing a puppy with one hand, then thrust it into Charlotte's arms.  She started to withdraw her hand, paused, then said, ``It's a loan.''



``Of course,'' Charlotte said.  She held the puppy close, scratched it behind the ear.  She knew better than to argue the point.



``You?'' Bitch asked Danny.



``No, thank you.''



``You don't miss your daughter?'' Bitch asked, narrowing her eyes a little.



``I do, I mean, I think I'll see her soon, probably, but--''



``Then take it.  For now.''



He surrendered in the face of her blunt approach, accepting the puppy.



``The kids,'' Charlotte said.  ``They've already settled in bed, but I think they'd \emph{love} to have a visit with the puppies.  Tell them it's just for a little while, they can cuddle, but they have to stay in bed.  Oh, and they don't know how to play with dogs, so be sure to teach them the ground rules, okay?''



Bitch nodded, then marched off with her new mission, the puppies leaping and falling over each other to keep up.



``Parian?'' Tattletale asked.  ``Supervise?''



Parian nodded.  She got down from the stool, and was joined by Flechette in heading to the back room.



``Well handled,'' Tattletale said.  ``She--''



She paused as the children in the other room started squealing and shouting.  Bitch's barked orders could be heard over the racket.



``--doesn't know how to handle this.  We're sort of forging new ground, but I think time's the only thing that's going to mend this wound.  I think she's hurting more than anyone, right now.''



Charlotte nodded.



Danny, though, said, ``Isn't that a little presumptuous?''



``I can \emph{do} presumptuous,'' Tattletale said.  ``Just trust me on this count, okay?''



Regent and Imp approached from the kitchen, finding spots on the floor of the living room to sit, just to the left of the television.  They had arms full of snacks, including the little gummy candies Charlotte had been planning to give the kids in their school lunches.



She'd figure something else out.  Best not to get distracted.  The puppies would suffice as a treat for the kids right now.



\emph{Damn it, they're going to ask to keep them,} Charlotte thought.  She scratched the puppy that now slept in her arms.



Grue stretched a hand in the direction of the pair, an unspoken request for one bag of snacks.  Imp replied by hurling a small bag of chips at him, with the same sort of movement that might accompany throwing a baseball.  It banked off of his helmet and fell behind the couch.



Grue grumbled, but he turned around to grab it.



Forrest arrived from the bedroom, pausing a second to take in the crowd in the living room.



``Okay, let's get down to business,'' Tattletale said.  ``Forrest, Charlotte, we're backing you up, on Taylor's behalf.  As of now, the Boardwalk doesn't fall in just one person's territory.  Parian, Grue and I will each have a hand in protecting it.  As of tonight, it should be the safest place in the city.  That's all already handled.  You'll have our numbers, in case of emergency, but you should only use it if there's real trouble.  Supervillains attacking or something like that.  This all goes more smoothly if we don't maintain any obvious connection between our groups that can be exploited.''



Charlotte nodded.



``Sierra is working under me.  She holds the property and presents our legitimate face to the public.''



Charlotte glanced at Sierra, who nodded.



``Property?'' Charlotte asked.



``Everything we own in Brockton Bay, through a series of dummy corporations, is officially in her name.  That includes the areas in the Boardwalk that Coil once controlled.  From now on, you can contact us through her for all of the basics.  I know Skitter arranged a way for those who contribute to the restoration of the Boardwalk to earn shares of property.  Sierra will see to that.  In a pinch, you can also talk to her about funding, big projects, and the like.  But I don't think it'll come to that.''



Forrest frowned.  ``Why not?''



``Skitter arranged for her territory to be taken care of,'' Tattletale said.



``She left us some money.  For food, to pay people.  Not a lot, but things should be sustainable by the time we run out.''



``There's more,'' Tattletale said.  ``She had a lot of money to spare.  Some from illicit activity, more from the properties we acquired and sold.  That's going to \emph{you}.''



``Wait, \emph{us}?''



``To the Boardwalk.  She mentioned getting the ferry up and running again, a new set of storefronts, and pushing for more residential areas.  Duplexes, apartments, condos\ldots''



``How much?''



``More than enough.  Part of the procedures for joining the Wards includes a full background check.  They'll find out she had a lot of money, much of it illicit, and they'll empty her accounts.  It might not be a problem, but I recently changed to a different bank, so to speak, and they're liable to find Skitter's end of the paper trail.'' Tattletale said.



Charlotte nodded.



``Something to use to take care of yourselves.  And the kids,'' Tattletale said.



Charlotte thought to what Scott had said.  Had Taylor blamed herself after all?  Was this a way of making amends?



``Part of the measures we'll have for defending the Boardwalk will be the mercenaries I have on retainer,'' Tattletale said.  ``Non-powered individuals, though they have experience fighting capes.  They're going to train your people.''



``Train?''



``In hand to hand, first aid, firearms and tactics for fighting bigger threats.''



Ethan reappeared in the front hall, hands jammed in his pockets.  His eyes went wide as he took in the supervillains sitting in the area where he'd been watching TV not twenty minutes ago.  Charlotte stood and ushered him towards the bedrooms.



Behind her, Forrest said, ``That seems like it'll cause more problems than it solves.  People are resentful.  There's already cracks forming.''



``Discipline will help with that,'' Grue said.  ``Time will help with the rest.''



``It's not perfect,'' Tattletale said, ``The rest, we can figure out.  What's important is getting the foundation laid out, and being ready.  Shit's going to go down when villains start making plays for the interdimensional door.''



Charlotte studied the people who were sitting around the room.  Concern, worry, anxiousness.  ``Are we going to make it?''



``Have to,'' Tattletale said.  She turned her head.  Bitch was returning from the back room.  She had only one puppy with her.  The wolf cub.  ``Taylor won't forgive us if we don't.''



``You should know.  When I was there,'' Danny spoke up.  ``Alexandria offered her a hell of a deal.  Two years of juvenile detention, and leaving the rest of you alone.  It wasn't everything she'd asked for.  She said no, said she trusted you to handle things on your end.  I don't want to be offensive, but I couldn't understand it.  Still can't.  But I thought you should know.''



``She was prepared to leave us to our own devices when she surrendered,'' Tattletale said.  ``But if she believes in us to that degree, that's another reason we can't fail.''



There were nods all around.



The discussion continued, but fatigue caught up to Charlotte at the same time that the details seemed to grow even more trivial.  Bitch, for her part, was focused, listening intently, while Danny seemed reserved, not quite a part of this.



Was this influencing his decision?  Which way would it, if it did?



It was midnight by the time they finished.  Exhausted though they hadn't fought anyone, weary Undersiders rose from their seats on the furniture and floors to make their way to the front door.



Charlotte accompanied Bitch to the bedroom, making her way to each bunk bed to collect a puppy, despite whispered protests and whimpers.  A tiny heartbreak, each step of the way.



\emph{I'm going to have to get these kids dogs now}, she thought, swearing to herself.



``Puppy therapy,'' she murmured, on her way back to the front hall.  Bitch was clipping the leashes onto the puppies.



``Mm,'' Bitch grunted.



``Does it work?''



``Yes,'' Bitch said.  ``But it's not enough.  I haven't felt like this since\ldots Brutus and Judas.''



Brutus and Judas?  Charlotte didn't recognize the names.  ``That's natural, isn't it?  We're people, we need other people close to us.  A dog is\ldots fantastic, but it can't fill that void.''



Charlotte could see a crease in between Bitch's eyebrows, but the look didn't reach her eyes or mouth.



``Did I say something wrong?''



Bitch shook her head, but she didn't reply.



``If you wanted to bring the dogs back, the kids would love it,'' Charlotte said.  ``And\ldots I'm thinking we'll have to get at least one to keep.  I think it could do them a lot of good, and they'd give the puppies more than enough love and care.''



Bitch's silence extended for long seconds.  She looked down at the puppies.  ``Maybe.''



``Maybe?''



Bitch shrugged.  She glowered at the ground, ``She wanted me to go to the other side.''



``First I'm hearing of this,'' Grue said.



``Through the portal,'' Bitch said. ``Police it.  Keep that side safe.''



``There won't be anything over there for at least a few weeks or months,'' Tattletale said.



The glower deepened.  ``That\ldots sounds good.''



``All on your own?'' Charlotte asked, ``But--''



``Me and my dogs,'' Bitch said.  Then she seemed to think of something.  ``Maybe.''



``We'll figure it out,'' Tattletale said.



With that done, the Undersiders departed.



Danny met Charlotte's eyes.



``Decided?''



Danny shook his head.



``Could be that she did it for you,'' she said.  ``I think even Tattletale was surprised she went over to the other side.''



Danny didn't reply.



``Good luck, either way.''



``You too,'' he answered.



``We survived,'' Forrest said.



``We survived,'' Charlotte said.  ``You'll be by in the morning?''



Forrest nodded.



She waited until he was gone, then closed the shutter, being careful to lock it.



Then she ascended to the top floor, past Skitter's room, with the now-empty terrariums and the armor stand with her old suit.  She reached the top floor, where Skitter's belongings had been collected and boxed.



\emph{I'd meant to show this to Danny}, \emph{to see if there was anything he wanted to keep or to send to her.}



She lay in her bed, Skitter's old room, but sleep didn't find her.  She was still awake when her alarm buzzed.  She rose and made her way downstairs to the bedroom.  Checking on the kids.



Jessie's bunk, dry.



No food under Mai's pillow, or at the end of her bed.  The girl had taken to hoarding food.



Others were asleep, though Ethan's eyes were open, staring.  She pulled his covers up a bit, and he smiled in the dark.



Aidan was awake too.



``I want a dog,'' he whispered.



``I know,'' she whispered back.  ``No nightmares?''



``Not any really bad ones since\ldots five nights ago.''



``Five nights ago?''



``Had a good dream.  A big dream.''



``About?''



He shook his head.  ``Can't really remember.''



``Okay,'' she whispered back.  ``Not a big deal.''



``But you told me to draw things or write them down after a bad dream,'' he said.  He pulled a pad of paper from the gap between his bunk and the wall.



She looked at it.  It didn't look like much of anything.  Two scribbles, circles and dots.



``These big things\ldots Fish?''



``I don't remember.  I think it started as a bad dream, and then became better.''



``And these dots or circles?''  They only covered part of the page.



``Planets and stars.  I only remember because that's how I usually draw them.''



``What do you mean, you only remember?''



``Forgot.  Even faster than I usually forget the bad dreams.''



She frowned.  The way he described it, it put her in mind of something.  The day Skitter had rescued her.  Someone had had a trigger event, and both Skitter and Tattletale had reacted.



The way the two had forgotten, and the things Tattletale had mumbled about while she was recuperating\ldots



``You don't have superpowers, do you?'' she whispered.



Aidan shook his head.



``You're sure?''



``Yes,'' he said, in a very solemn manner.



If it wasn't a trigger event, then what?



``Five nights ago?''



``I know because it was the night Skitter stayed out all night.  I woke up a bit after she came in.  I was drawing while she made noise in the kitchen.''



The night Skitter had been outed.  Where had she been, and how did it connect?



If not a trigger event, the \emph{potential }to trigger?



So many questions, and Skitter was no longer here to answer them.





