





\strong{March 2nd, 1997}



``Okay,'' Daiichi said.  His Japanese was easy, a lazy drawl.  He paused at the top of the flight of stairs, sneering a touch as he waited for his followers to ascend.  ``If you don't hurry, they'll be gone by the time we get there.''



There were grumbles from the others.



``Why isn't there an elevator?'' Ren whined.  Of all of them, he was the heaviest, the black jacket of his school uniform straining across his shoulders.  He'd dyed his hair blond, but hadn't yet found a good style to wear it.  Ren was Daiichi's lieutenant; most thought that was because Daiichi put too much stock in Ren's size, ignoring the fact that he was more fat than muscular.  People who knew Daiichi better speculated that it was because Daiichi wanted someone fat and ugly that could offset his own good looks.  Only those inside Daiichi's group and the people who crossed them knew better.



``Only three floors,'' Daiichi said.  ``And we wouldn't use it if they had one.  They could have someone watching.''



``With only two of them?''  Ryo asked.



``Can't hurt to be safe,'' Arata said.



Kenta was the first up the flight of stairs.  Daiichi clapped one hand on his shoulder.  Their leader asked, ``Ready?''



``Ready,'' Kenta answered.  His heart pounded.



For others, for his neighbors and peers, conformity was safety.  To be the same as one's peers, it reassured the self, reassured others.  Standing out was bad.



But Kenta stood out anyways.  He looked different.  People knew his mother was Chinese.  He was oddly tall for his age, his grades poor.  He could have struggled, but there was so little point.  He was competing with classmates who were already miles ahead of him, who were fighting to keep ahead of one another by studying after school, studying at night.



This was something else.  It was both thrilling and terrifying, to recognize those lines and ignore them.  To be brazen, to stand out on purpose.  Breaking rules, breaking convention.  He imagined it was like the rush that accompanied a fall to open water or hard ground.



``This is our springtime,'' Daiichi said, and he managed to say it without sounding ridiculous.  At seventeen, he was older than any of them.



\emph{Springtime}, Kenta thought.  Daiichi had it all planned out.  They would earn a reputation for themselves, then submit themselves to the Yakuza.  With luck, they would be accepted as low-level members of the `chivalrous organization'.  The freedom would be gone, in a way.  Their `springtime', in a sense, referred to the brief period where they were free to do what they wanted, between the confines of school and membership in the Yakuza.



``There's only two Chinese?'' Ren asked, as they filed out of the stairwell and into the restaurant on the third floor.  The rooms here had thick walls and a wooden door, rather than the traditional paper.  They'd wanted privacy, maybe.  It didn't matter.



``My cousin owns the building,'' Daiichi said. ``He said they paid with bundles of bills, and no other Chinese came in.  Some Western \emph{gaijin}, but nobody threatening.''



Kenta looked back at their group.  Nine people for two men?  And they had an unfair advantage, besides.



``Go,'' Daiichi ordered.



Kenta was stronger than Ren, so he was the one to kick down the door.  He moved aside to let fat Ren advance.  He wasn't stupid, wasn't ignoring the possibility the foreigners had guns.  



There was no gunfire.  Instead, he could hear someone speaking in English, very calm.



``\emph{The woman is upset you did not take enough precautions},'' A man said, in Chinese.  He sounded more alarmed than the English speaker.



Daiichi and Ren led the advance into the back room.  Kenta followed, looking over Ren's shoulder to take in the scene.



There were five people in the room.  Two were Chinese, sure enough.  Businessmen, they seemed to be, kneeling on one side of a squat dining table that was neatly stacked with cash and `bricks' of white powder in plastic wrap, as well as various dishes laid out with vegetables and meat.  A Japanese man sat at one end of the table, hands folded in his lap, eyes wide.



But there were two more \emph{gaijin }in the room, kneeling opposite the Chinese foreigners.  A black woman in a white suit jacket and a knee-length dress, and a twenty-something woman with a European cast to her features, with dark hair and a black suit.



The black woman spoke, and the Japanese man translated it to Chinese.  ``\emph{The woman recommends we stand back.  Her bodyguard will take care of the situation}.''



``The woman in front is a bodyguard,'' Kenta told Daiichi.



This was wrong.  The two women were too confident.



Daiichi drew a gun and pointed it at the woman.  Kenta felt his heart leap at the sight of the weapon.



Then Daiichi fired, a warning shot.  Kenta flinched despite himself.  He'd never heard a gunshot before.  Loud.



The men were cowering, trying to hide beneath the table.  The women hadn't even reacted.



``One bodyguard?'' Daiichi asked, sneering.  He made the first move.  He flared a brilliant green, then jolted as a phantom replica of himself leaped forth.



The phantom Daiichi flew across the room like living lightning, a trail of neon green smoke in its wake.



The bodyguard was already moving, her hand on a plate.  She turned it upside-down and threw it in a single motion, and it caught the air like a frisbee.  It turned in mid-air and crashed into the real Daiichi's face.



He staggered, and the phantom he'd created dissipated a fraction of a second before reaching the bodyguard.  She shut her eyes as the residual smoke carried past her.



Kenta stared.  He'd never seen Daiichi's ability fail him like that.



Daiichi raised the gun, and the woman raised one knife from the table, turning it around so she held the blade, the metal handle extended.  She held it out with one hand, pointing it at Daiichi's shoulder.



Daiichi fired, and the knife went flying.  It ricocheted, spinning rapidly, striking the doorframe behind the bodyguard before flying over her head in a tall arc.  She caught it in her other hand, resuming the exact same position as before, then shook her right hand for a second.



She said something, murmuring it in English.  The knife, still held in front of her, had a dent on the end.



The black woman behind her said something else.



``What are they saying?'' Daiichi asked.



``The woman in the suit just got permission to kill us,'' Hisoka said.  ``But the black one said not to spill any blood.''



``We should run,'' Kenta said.



``You scared?'' Daiichi asked.  ``We have muscle.''



``So does she,'' Kenta retorted.



Daiichi only smirked.



\emph{Can't run, we're going to get hurt if we stay\ldots}



Ren rolled his shoulders, then \emph{inhaled}.



Wind rushed out of the room, and small objects were drawn towards Ren.  The intensity of the suction grew as the fat boy sucked in more and more air.



The bodyguard kicked one edge of the low table, and the wind caught it, helping it rise.  Money, plates and the bricks of white powder slid to the floor, sliding and rolling towards Ren.



Daiichi opened fire again, indiscriminate, but she didn't even react.  Her knife blocked one shot that was directed more at the black woman, flying out of her grip, and the bodyguard walked between the rest of the shots without even dodging.  She seized a table leg in one hand.  It would have been too heavy to lift, but Ren's suction was hauling it off the ground.  Two bullets bit into the thick wood.



Daiichi unleashed his power, creating another ghostly replica of himself, incredibly fast, stronger than he was.



The woman kicked the table, and it spun through the air as it flew towards Ren, clipping the ghost.  The phantom lost an arm and a chunk of its chest, got its bearings, then charged the bodyguard.  The damage to its chest was too grave, and it crumpled into neon green dust a pace away from her.



Ren was struck by the moving table, hit with enough force that he stumbled backwards into Kenta, Hisoka, and the other mundane members of the group.



Ren \emph{blew}, and the table went flying across the room.  Kenta's heart sank as he saw the woman, crouching low to the ground.  Her hand reached up to strike the flying table, altering its course as it flew towards the Chinese men.  It came so close to hitting them that Kenta thought it would be like the cartoons, where someone was cut but didn't start bleeding until seconds had passed.



Except it hadn't hit them, and the woman was too close to the ground to really be affected by the wind.



``Suck!'' Daiichi shouted.



``Don't!'' Kenta said, though there was little point.



It was too late.  Ren had stopped blowing, buying her a second to move.  She stepped forward, closing the distance to the group.  Daiichi created a \emph{third} ghost, rushing towards her, but she avoided the first strike.



Ren started drawing air in once more.  Daiichi's spirit opened with a flurry of attacks, moving twice as fast as she was, but failed to land a strike.  The bodyguard took a step back and used the toe of her glossy black shoes to flick a brick of powder into the air.  She threw it, and the suction only added to its velocity as it soared to Ren's right.



Daiichi's spirit was fast enough to avoid the brick, but Daiichi wasn't.  It bounced off his head, and the ghost dissipated again.  She kicked the table, and again, the suction caught it.  It flew into Ren's shins, and he fell.



Thrice, both the ghost and Ren had been countered, almost \emph{casually}.



Daiichi shouted, uncharacteristically angry.  Uncharacteristic, maybe, because he'd never lost a fight before.



The others pushed forward from behind Kenta.  Had they not just seen the fight?  They really thought they'd accomplish something?



But the force of the others charging forward from behind started him moving forward, and he was driven to \emph{keep} advancing by the vague, incoherent idea of what might happen to him if he, the largest, physically strongest member of Daiichi's group, turned coward.



He knew in an instant that it was a mistake.  Daiichi's ghost, twice as fast and twice as strong as Daiichi himself, an expendable assailant, hadn't accomplished anything.  Why would six or seven teenaged delinquents?



She tore through them, every movement precisely calculated to disable, to crush, blind, stun and stagger.  They were driven to stumble into one another, their weapons knocked from their hands.  She wasn't any faster than any of them, not a martial artist, though there was a degree of elegance to what she did.  No movement wasted.



Her foot caught Kenta in the diaphragm.  She planted one hand on the back of his head as he winced from the blow, then pushed him face first into the ground.



His teeth bit into a brick of powder, puncturing the plastic itself.  Kenta tried to rise, but she stepped on the back of his head, driving him facefirst into the brick a second time, hard.



Someone else fell to the ground a short distance away.  Kenta turned to look, simultaneously coughed, and loose powder exploded around his face, filling his eyes.



The powder caked his nose, thick in his mouth, to the point that he couldn't swallow.



Drugs weren't a `big' thing in the East, even among gangs.  He didn't know the particulars of any powder or substance.  Only that they were bad, possibly lethal if too much was ingested.  He tried to spit it out, but couldn't help but feel like he was swallowing more than he was removing.  The weight of the woman bodyguard was on his head, holding him there, suffocating.



He felt the rush of it taking hold, intense and seemingly without a ceiling to top it off.  His face in the dirt, in the \emph{dust}, he was overwhelmed by the paradoxical sense of being like the king of the world.



That rush lasted too short a time.  He could feel the rush building until it felt like his heart was going to burst or vibrate itself into pieces.  He felt nauseous, as if he was going to throw up, but couldn't bring himself to.



Kenta's left arm started going numb.  He knew what that meant.



With a cold feeling in his churning gut, he thought, \emph{I'm having a heart att}–



He found himself out of his body.  He was an observer, an outside agent, without body or mind.  He couldn't \emph{think}.  He could only exist, as a part of some sequence of events.



Two entities, communicating in increasingly short bursts as they drew together.  Two entities, each unfolding and folding through realities, through multiple worlds at the same time.  Two entities, singing ideas through mediums he could barely comprehend.  Through light and heat and space and half-lives and gravity.



And they were \emph{looking}.  Looking at a planet that was broad, more gas than solid.  A world of perpetual storms.  There were lifeforms in there, lifeforms in countless possible variations of that world.  Bloated bags of gas that flowed through and in the storms, in kalleidoscopic patterns.



He could see what they were focusing on, see them examining those possible worlds, declaring something.  Ownership here.  Claim there.  Territory elsewhere.



–\emph{ack.}



Kenta's thoughts were confused as he felt the high seize him.  Three things overwhelming him at once.  The things he'd just seen, fleeing from his recollection.  His own body, dying in a violent, incomprehensible way.  The world beyond-



He blinked the dust out of his eyes, felt them burn, could only see shadows, could only hear the rush of blood in his ears.



The bodyguard had stepped away from him, freeing him to raise his head.  She'd staggered, and was being supported by the black woman.



He turned away, flipping himself over.  He could see the fat shape of Ren, on his hands and knees, Daiichi prone on the ground.



The bodyguard recovered faster.  She found her stride quickly enough.



She kicked at Daiichi's throat, hard.  Ren, she struck in the nose with one boot.



The black woman said something in English.



``\emph{S-she'll take the cost of the lost product out of the deal,}'' the translator said in Chinese, his voice distant.



Kenta only lay there, his chest heaving.  He felt stronger, could feel his heart returning to some form of equilibrium.



But he knew he couldn't win.  He lay there, doing his best to emulate the dying, as the Chinese men collected both cash and drugs in a bag, handing them to the black woman.



She spoke, and the Japanese man translated it to, ``She would like to discuss delivery of the product on the way out.''



Kenta lay there long after the two women and the Chinese men had left.  He wiped caked powder from his face, though the effects had receded, the tingling and the rush long since faded.  Whatever had happened to him, the drugs did almost nothing, now.



He wiped his face with his shirt, then checked on his friends.



Daiichi, dead, suffocated, eyes bulging.  Ren lay there, eyes rolled up into his skull, his nose rammed into his brain, though the blood hadn't leaked past the aperture of his nostrils.



Hisoka, suffocated on powder, as Kenta almost had.  Arata, gasping for air he couldn't seem to pull into his lungs.  Ryo's head had a dent in it, and his eyes were unfocused.  Jirou's airway had been blocked, much as Daiichi's had.  Both Takeo and Shuji lay dead with no apparent wounds.



All dead or dying, with no blood spilled.  Technically.



Kenta waited, holding Arata's hand as the boy slowly died, then he straightened.



\emph{Idiots}, he thought, with a degree of anger.  It had been foolish to escalate the fight after seeing what the woman was capable of.  He'd be more careful of who he fought in the future.



\blacksquare



\strong{November 2nd, 1999}



Lung toyed with a flame in one of his hands as he watched the great lizard-man's rampage.



The \emph{Sentai Elite }were battling the thing, assisted by the \emph{gaijin} heroes.  Once every few minutes, someone passed him, flying, carrying wounded.  Lung didn't care.  It was about timing.  If he was going to do this, he'd do it right.



A tidal wave rocked the area, and Lung had to hold on to a nearby building to keep from falling.  Heroes were swept up in the wash of water, and buildings were leveled.



The anticipation of a fight stirred inside him.  He could feel the scales beneath his skin, just \emph{itching} to be brought to the surface.  The fire, too, was warm in the core of his body.



This was a fight that was worthy of him.  The trick was orchestrating it so he wouldn't die before he got strong enough.  It was his biggest drawback.  The fight\ldots the heroes were stalling in their own way as well.  He could tell by the way the heroes moved.  They fought in shifts.



Eidolon was fighting now.  He hurled globes of energy the size of small houses at Leviathan, and each one was sufficient to knock the creature away, flaying away the thing's skin and simultaneously slowing it.  The hero's own hydrokinesis deflected the lizard's ranged attacks, diverting them skyward or off to one side.  Leviathan couldn't attack from range, and couldn't get close without getting pummeled.  He attempted to run, only for Japan's foremost team, the Sentai Elite, to step into his way, blocking his progress.



``Are you fighting?''



Lung turned to look at the speaker.  A woman in a yellow and black Sentai costume.



``Yes,'' he answered, his voice a rumble.  His power had granted him additional strength, durability, regeneration and control over fire even in his ordinary form, but the changes to his body had altered his voice.



She glanced at the fight, as if unsure whether she should be participating or talking to Lung, ``You're a yankee?''



``No.''



``You're a villain?''



``I am me.''



Another tidal wave rocked the area.  This time, the water reached Lung, sweeping up to waist level and forcing him to hold the windowsill again to avoid losing his footing.  He caught the Sentai woman's wrist to keep her from being washed away.



He could feel the scales beneath his skin stirring, threatening to rise, \emph{eager}.



``Sumimasen deshita,'' she said, once the water was mostly gone.



Lung only grunted a response.



``Why are you back here?''



``I'm waiting,'' he answered.  ``And you should be fighting.''



``I can't do anything.  My power hurts people, but it doesn't hurt \emph{him}.  I'm not permitted to leave.''



The heroes were winning, slowly but surely.  Slowly more than anything.  Each tidal wave was doing catastrophic damage in the meantime.



\emph{I'll fight}, he thought.



With that very thought, his power started stirring into effect.  The scales began growing, slowly but surely, bristling like a sea urchin's spines as they arranged themselves.  The very \emph{anticipation} of the fight was serving to fuel his abilities.  When he changed, it would be rapid, accelerated by the sheer \emph{threat} his opponent posed.



He abandoned his handhold and began striding through the flooded streets, towards Leviathan and the others.



He'd made a promise to himself.  He wouldn't lose again.  Victory, it didn't matter.  But \emph{losing}?  He wouldn't accept it, not like the loss he'd faced at the hands of the unnamed woman.



And that very thought, that certainty, it stirred his power further, as though it were something alive, something \emph{other}.



Another tidal wave hit.  Leviathan disappeared in the midst of it, reappearing elsewhere.  Lung could hear the destruction as the beast clawed and tore through the base of one building that heroes were perched on.  He quickened his pace, felt himself growing stronger as he got closer.



The beast was otherwise occupied\ldots this was the time.



``You're going to die!'' the Sentai in black and yellow shouted.



\emph{I'll never die}, Lung thought.  \emph{I might fall, but I'll come back again and again.  I might falter, but I'll return with twice the fury}.



The waves were more frequent now.  Buildings here had been built to tight specifications, to remain standing in the face of earthquakes and tsunamis, but it wasn't enough.  Barely a minute passed between the strikes, with each wave reaching further inland than the last, and only a handful of buildings stood at their full height, where there had been a city here only an hour ago.



It was in one of those brief moments of respite that the ground shuddered.  Lung nearly lost his footing.  When he looked up at the night sky, he could see that the tallest standing buildings were swaying, like fronds bending in the wind.



Somewhere he couldn't see in the gloom, a building swayed too far and crashed to the ground.



Eidolon backed off, and Alexandria stepped in, flying into close quarters with the beast, battering him.  He tried to duck beneath the water, but she broke off to fly beneath, using her strength and the speed of her flight to part the water, cutting off his retreat.  He slowed as he entered open air, though \emph{slow} wasn't the word.  Legend caught him square in the chest, and Leviathan slowed long enough for Alexandria to catch him by the tail.



She flew straight up, holding the monster by the tail.  Between Leviathan's dark scales and Alexandria's black costume, they disappeared in the gloom.



Leviathan fell, and the resulting impact was oddly out of sync with his mass.  The water in particular seemed to react, a single ripple extending outward, clearing an area around him of any and all water.



Lung braced himself, felt the water collide with him with a force like a locomotive, was summarily dragged beneath, trapped, suffocating.



Scales pierced his skin, strength surged through him, and his pyrokinesis boiled around him, disrupting the water's flow, rendering it to steam.



Other heroes were pushed back a hundred meters, but Lung was already standing, burning himself dry, advancing on the fight, where Eidolon was again engaging with Leviathan.



Another tidal wave struck, barely giving the defending forces time to recover from the last assault.  Lung lost his footing, lost another dozen feet of headway.



More scales were sprouting, they were growing en masse now.  His blood coursed through his veins at twice the usual speed.  Fire burned around him perpetually now.  He was naked, the burned rags of his clothes swept away by water, and he didn't care.  He was in freefall, of a sort, but it wasn't the ground waiting for him.  It was Leviathan.



His flame blasted out to pelt the Endbringer.  It didn't do any substantial damage.



Lung ran, and it took him an instant to get used to his newfound strength, to find a stride and a rhythm.



The ground was shaking almost constantly, now.  The lasers, Eidolon's strikes, the very impacts of the blows Alexandria delivered, the Sentai's attacks, the barrages from assisting heroes.  A cacaphony of noise, light and violence.



He struck Leviathan, and was struck in turn, his bones broken, internal organs smashed.



He very nearly blacked out, but his rage won out.  He struggled to his feet, found one femur in two distinct pieces.  He knelt instead, resting his weight on one knee, the other foot planted on the ground, taloned toes biting into asphalt, and he directed a constant stream of fire at the Endbringer.



A flick of Leviathan's tail sent him sprawling.



But Lung knew he'd reached a critical point.  His leg was already healing, the changes speeding up.  He stopped to hold his leg, pull the bones into what was more or less the right position, so they could bond.



\emph{Anyone who crosses me will pay twice over}, he thought.



A Sentai in purple and green offered him a hand.  Lung ignored the man, standing on his own.  Again, a stream of fire, but the color was more blue than red.



The Sentai joined him, adding their ranged fire to his.  They had a man who mass produced their armor and weapons, each with wrist-mounted laser guns, rifles at their hips.  Sixteen or seventeen of them opened fire with both weapons at the same time.



Leviathan turned, struck.  Some Sentai used powers to soften or deflect the incoming scythe of water.



Leviathan charged, and Lung stepped forward to meet the brute, roared in defiance.



He wasn't strong enough.  Leviathan knocked him aside, and Lung rolled, putting taloned hands and feet beneath him before rushing forward, shallow leaps that carried him over the water that was knee-high to the humans.  Barely halfway up Lung's own calves.



He found handholds in the shallow wounds on Leviathan's back and shoulders.  The abomination moved, and the watery echo that followed its movements crashed into Lung.  Not enough to unseat him.



The tidal wave that struck wasn't enough either, nor Leviathan's speed as the creature swam.  Lung dug deeper, clawed flesh away.  Deeper in Leviathan's body, the flesh was only harder, the ichor making it slick.



Lung roared, burned head to toe as he clawed deeper still.  If Leviathan's muscle was as hard as steel, Lung would burn hot enough to melt steel.



Leviathan surfaced, and Lung found his way up to the monster's neck.  He tried to reach around, and his arm shifted, reconfiguring to be a fraction longer.  Lung's legs, arms, and talons were growing as well.



\emph{Stronger, larger}.  Another man might have been afraid of what he was becoming, but this was only continuing the freefall.  \emph{Freedom.}



Leviathan shook him free, and Lung found no trouble in putting his feet under him.  His mouth strained, opened wider than it should have, four individual mouthparts flexing, bristling with teeth, his own lips buried somewhere deep inside, altered.



Water steamed and boiled around Lung's calves as he stood as straight as he was able.  He'd changed more, his shoulders broadening, his chest heavy with muscle.  He had to rest his taloned hands on the ground to maintain his balance.  His senses focused on Leviathan like a laser, taking in everything, even the faint creaking of the monster's movements and the Sentai's muscles, and the infintesmally small burbles of ichor bubbling forth from Leviathan's wounds.



The ground was rumbling constantly, to the point that the local heroes were starting to seem more concerned about the landscape than about Leviathan.



There was a crack, and Lung was put in mind of the gun Daiichi had fired, more than two years ago.  A loud sound, a \emph{wrong} sound.



The ground shifted underfoot.  Heroes scrambled for cover, scrambled to run or save their friends, and water rushed forth.  Lung merely set his taloned toes in the ground, ignoring the water, the debris, and the people that flowed past him.



Leviathan charged him.



\emph{He can't ignore me now}, Lung thought.  He was only half the height of the Endbringer, but it was enough.  Fire against water, claw against claw.  Leviathan hit harder, but Lung healed faster.  Every second he fought without Leviathan tearing him in half was a second that was to his advantage.



The ground parted, and Lung could hear the water rushing in to fill the void.  The landmass had parted, and ocean water was streaming in from miles away.



Leviathan tried to drag him closer to the chasm, no doubt wanting to fight in that churning abyss.  Lung planted toes in the ground and resisted.



Alexandria was there in a heartbeat, helping, keeping Leviathan from finding his way inside.  She drove the monster back, bought Lung purchase.



She said something in English, but Lung didn't know the language.  The only others who spoke Japanese or Chinese were gone, now.  They'd evacuated who they could, and the remainder were left to drown.  The only ones left were the indomitable, and for now, Lung was among them.  They fought to keep Leviathan from continuing his rampage, to keep him from carrying on until he'd wiped away all of Japan.  Lung just \emph{fought}.



Fought for minutes, hours.  Fought until four wings extended from his back, and he burned so hot that the steel-like flesh just beneath Leviathan's skin was blackening and charring to ash by proximity alone.  Until he was \emph{larger} than Leviathan, until even \emph{Alexandria }hesitated to get too close.



For that indeterminate period of time, Lung was king of the world.



But he began to weaken.  The lesser heroes were gone, washed away or helping others to evacuate, the greater heroes a distance away.



And Lung had nothing to fuel his power.  He was engaged in a fight of ten times the scale he'd been in before, and his power was leaving him.



The landmass disappeared beneath the pair of them, the shards of land drawn beneath the waves, and Lung was now fighting Leviathan in the monster's home ground.



For an instant, he thought he would die.  But Leviathan, wounded, broke away and fled into the depths.



Lung only sank, too dense to float, growing wearier by the second as his power left him, the fight over.



He'd expected a feeling of satisfaction, but he knew he hadn't delivered a killing blow, that he had been a long, long way from it, though he'd done more damage than anyone had in years.



His enemy couldn't be killed.  Lung had become something more terrifying than the Endbringer, but there had been nobody to see.  None of the public to recognize him, to respect and fear him.



He sank, feeling a kind of despair.  Too tired to move, he touched bottom.



Alexandria found him in the depths and brought him to the surface.



\blacksquare



\strong{August 13th, 2002}



The walls of the C.U.I. prison loomed around him.



Lung fumed, but his power was denied him.  He paced, punched walls, burned the concrete with his power.  All around him, the area was pockmarked with the wounds that marked his periodic struggles.



They'd had him in regular cells before.  It had been a learning process for them.  He'd found that surviving in a prison like this involved being a true monster, so he'd bowed his head to one boss.  When this boss had discovered what he was capable of, he'd attacked another leader in the prison.  The ensuing war had ended with Lung being placed in higher security, until he fought the man who'd brought him food, very nearly escaping before T\textoverline{o}ng L\'{i}ng T\v{a}, who never showed herself, encased him in a mountain of stone.



All in all, three years since he'd fought Leviathan.  Two years since he and his mother had come here to Chaohu.  A year and eight months since he'd been arrested by the Y\`{a}ngb\v{a}n.



A year and \emph{four }months since T\textoverline{o}ng L\'{i}ng T\v{a} had buried him here at the base of this pit, with the same routine.  Twice a day, he would get two packages with food.  Every day, he would pace, trying to tap into his abilities, finding them beyond his reach.  He would struggle, fume, scream, and wonder if he was going mad with the solitude.  Sometimes it rained, and he found himself knee deep in water.  Sometimes it was cold enough he couldn't sleep.  Always, he was here, in a pit so deep that the hole at the top looked no larger than his handspan when he held his hand overhead.



Every seven days, T\textoverline{o}ng L\'{i}ng T\v{a} used her powers on the walls.  The floor, she left alone, but the walls were wiped clean, her power to manipulate stone turning the four impossibly tall walls of Lung's cell into flawlessly smooth surfaces.  She would absorb any and all of the trash that remained from his meals, any of the wildlife that had accidentally found their way into the pit, and all of Lung's leavings, which he customarily left in one corner of his cell.



Every fourteen days, like clockwork, the Y\`{a}ngb\v{a}n opened communications.



Lung was waiting, waiting for T\textoverline{o}ng L\'{i}ng T\v{a} to use her power.  Like a ripple traveling over the surface of water, he could see her power extend down the walls of his cell.  It touched the base of the wall and traveled along the floor.



Lung didn't resist as the ground swept over his legs, trapping him from the knee down.



They appeared, descending from above, floating.  Two of them this time.  They made no mention of his lack of clothes or his shaggy hair.  Both wore identical uniforms, red jackets and pants, their red masks turning their faces into overlarge, featureless gemstones with coverings over their ears



At each of their shoulders, there was a number.  One-six and two-seven.\emph{  }Not ones he'd met before.  No names.  No identities.



``\emph{Will you join us?}``



Always, the same questions, always in Chinese.  He didn't answer.



``\emph{The American heroes approached you.  What deals did you strike?}``



Again, he didn't answer.  He'd tried to tell them the truth, that he'd told the heroes to go away.  The Endbringers couldn't die.  There was no point to fighting them.  Twice they had approached him with better deals, promising him the world, but he'd turned them down twice in turn.  He'd considered the idea of taking the third offer, but then he'd followed his mother to the C.U.I. states and lost touch with the Americans.



Not a real concern.



``\emph{You will stay here until you answer our questions}.''



``\emph{I will join},'' he told them.



They exchanged a glance between them.



He moved one hand and saw them flinch.  They wouldn't burn any more than the other \emph{Y\`{a}ngb\v{a}n} members had, but they still \emph{feared }him.



It made him feel better than anything in the past long months.



``\emph{The Y\`{a}ngb\v{a}n is the solution,}'' the taller of the two said.  ``\emph{You agree this is truth}?''



``\emph{No},'' Lung said.



``\emph{That is a shame.''}



``\emph{I want out of here,}'' Lung told them.  ``\emph{That is all.  If I must kneel, I will}.''



``\emph{We need to hear the right answers before we can go any further.  We will come again in two weeks time and we will ask you again.  If you give us the answer we require, we can move on to the next step}.''



\emph{And}, Lung thought, \emph{carry down the chain of questions, steps, and procedures until I fail.  You will break me and brainwash me until I am one of you.}



Worst of all, they would take his powers, most of them, and give him others in turn.  This was the reason they imprisoned him, the reason they sought to break him.



He would risk it, and accept the offer.  He would do whatever they required of him, and then he would kill whoever he needed to and escape.



\blacksquare



\strong{March 23rd, 2011}



\emph{With every defeat, a matching ascent}.



``The `Azn Bad Boys' is a shit name,'' Bakuda said.



Lung didn't react, staring at her.



``Just saying.''



``It was the name of the group I joined when I came to America.''



``See, that's what I don't get.  You're a badass, fine.  You tested the waters, took on a whole team of local heroes, and you walked away.  Right?''



``I fought Armsmaster, Dauntless, Miss Militia, Velocity, Challenger, Assault and Battery,'' he said.  ``Yes.''



``Except you're small time.  You've got all this power, and what do you have to show for it?''



``Fear,'' he said.



``I don't fear you,'' Bakuda said.  Her pale blue eyes stared at Lung, unflinching.



``You will,'' he answered her.



She shrugged.  She paced, looking around the building.  Two of Lung's whores sat on a couch, looking distinctly uncomfortable, as if they didn't know how to hold themselves, the pose to take.



``There are two kinds of fear, Bakuda,'' Lung said.  ``The first is common.  Fear of the unknown.  A \emph{questioning fear}.''



``Uh huh,'' she said.  He could tell he had her attention.



``This is fear of unanswered questions.  If I fought him, would I win?  How is he going to hurt me?  Who or what is he?''



``And the other kind?''



``A fear of \emph{knowing}.  Of realities.  If I fight him, I lose.  I know him, and I quiver to be in his presence.  I know he will hurt me and I know it will be the worst pain imaginable.''



Bakuda didn't reply.



``I have found that the first is a weak fear.  It breaks.  It ends when you have answers, when others give you their support.  The other?  It is a fear that breeds itself.  It is a \emph{disease}, and it only gets stronger when you fight it and fail.  I have situated myself here to engender that kind of fear.  The residents know me.  Those I want for my gang, I take.  My influence grows, and my enemies know not to cross me, because I always have my vengeance.''



``But the `Azn Bad Boys'?''



``A reminder, to my enemies, of what I've done before, what I could do again.''



Bakuda frowned.



``I defeated many gangs, many groups.  Some had powered members, others did not.  I recruited some.  Oni Lee was one.  The rest I killed.''



``And the heroes didn't stop you?''



``The heroes see me as a double-edged sword.  \emph{They }fear me.  They know what I am capable of when the situation calls for it, they know I am too strong to defeat as a group.  For now, I wait.  They leave me be because the only aggression they can see is that I inflict on other criminals, and I amass power, swelling in reputation.''



``And the fact that you, a halfbreed, recruited me, a halfbreed, and built a gang of a bajillion different races, it's totally not a freudian thing, tying back to some childhood issues.''



``No,'' Lung growled.



Bakuda only smiled.  ``And what happens down the road?''



``I have enemies,'' Lung thought.  ``Those who have slighted me, those who have won.''



``Like Leviathan?''



Lung shook his head.  ``Leviathan, I beat, if you can even call it an enemy.  It is a force of nature.  No, I speak of other enemies, insults old and new.  I will defeat each of them in turn, and then I will rule.''



\emph{The woman in the suit, the Y\`{a}ngb\v{a}n.}



``So petty.  And you want me to help?''



``You \emph{will} help,'' Lung said.  ``Because you think like I do.  In terms of power and fear.''



Bakuda took a seat at the end of the couch.  The two whores inched away from her.



She smiled at that.  ``Alright.  You got me.''



\blacksquare



\strong{July 14th, 2011}



``\ldotsand that's the gist of it,'' Amelia said.



Lung watched Teacher's expression change as he considered the idea.  The man seemed so ordinary, so unassuming.  To hear the man talk about it, he'd been one of the foremost criminal masterminds until the heroes trumped up charges against him.



``I might not be explaining it right,'' Amelia said, ``How my power works, hard to interpret.  But I think I've worked it out.''



``I can see where it makes sense to you,'' Teacher said.  ``But for those of us with no conception of these power granting entities, we don't have enough solid ground to found the idea on.''



Amelia frowned.



Teacher shook his head.  ``There's holes in your logic.  The Endbringers?''



``I don't see how they fit in,'' she admitted.



``A developmental step forward?''



``No,'' Amelia said.



``A step backwards, then?''



``No.  At least, I don't think so.  Something else entirely.''



``To be frank,'' Teacher said, ``I don't know whether to hope you're right or wrong.''



``It's both,'' Amelia said.  ``It's bad, but at least we \emph{know} how bad.''



``With nothing we can do about it until someone lets us out,'' Teacher said.



Amelia frowned.  She rested her elbows on her knees, as she sat on the edge of Marquis' bed.  Plastic crinkled with the movement.  The tattoo artist who was working on her arms had scrounged up plastic sheets from the meals that came down the shafts, sterilizing them and then taping them in place.  The freshest tattoos and the irritated flesh around the markings were blurry just beneath.



Panacea had complained about how idiotic it was, because she couldn't get sick, but any artist had their rules and peculiarities, and Marquis had told her to accept them.



``Well,'' Marquis said.  ``It's food for thought.  I'd suggest a breakout attempt, given how grave this all seems, but we know how that tends to go.''



``Yes,'' Teacher agreed.  ``Our deal stands?  You won't replace my dentists or doctors?''



``That wasn't the deal,'' Marquis chided.  ``We'll price match.  A little competition will keep your employees honest.''



Teacher frowned.



``It's the best deal I'm willing to-''



Marquis stopped short.  Lung turned to see Spruce at the entryway into the cell.



``Hey, boss,'' Spruce said.



``What is it?'' Marquis asked.



Spruce gave him a curious look before turning back to Marquis, ``Big news. TV.''



Lung took his time walking down to the televisions.  Marquis, Spruce and Amelia made their way down, where a crowd had gathered to watch.  It was rare, that the same thing would be on all of the working televisions.



``\emph{It was due to a concerted effort this evening that we were able to stop Alexandria before more damage could be done.}''



``What's this?'' Amelia asked.  She gave Lung a nervous glance as he approached.



``Alexandria bit it,'' Cinderhands said.



With that, each of the new arrivals turned their attention to the screen.



``\ldots\emph{will recognize Taylor Hebert, revealed to be Skitter in a controversial confrontation at the school just a week ago, a confrontation Alexandria ordered.  Taylor Hebert played a crucial role in stopping Alexandria in a moment of crisis, ending the fight.}''



``No shitting way,'' Panacea said.



Lung remained quiet.



``She's the one who arrested you, isn't she?'' Cinderhands asked, looking over his shoulder at Lung.



``No,'' Lung said.  ``We fought twice, I was arrested by others.''



``But she beat you?''  Cinderhands asked.



``Shush, C.H.,'' Marquis said.



''\emph{It marks change, and it marks a step forward.  A chance to fight Endbringers and other threats without sabotage, without worrying who stands beside us, or whether our leadership is compromised.}''



``Anyone else thinking that we \emph{really} should get a chance to appeal our cases?''  someone in the crowd asked.  ``If the organization is this fucked up, the arrests can't count.''



``Yes,'' Marquis said, his tone condescending, ``I'm quite sure the Protectorate will be apologizing to the public, then they'll throw open the Birdcage's doors and let us all loose.''



``\ldots\emph{hope.  We've investigated the portal to another world, and confirmed that there are resources and even shelter, a possibility of escape in a time of emergency\ldots}''



``\emph{And new allies, as unlikely as they might be.}''



Panacea stared as the girl on the television stepped forward at Chevalier's bidding, She removed the black sweatshirt and pants the PRT had issued her, revealing a costume of white and gray beneath.



Amelia's hands went to her mouth.



Marquis glanced at Amelia.  Lung took that glance in all it's import.  The two girls were opposite sides of the same coin.



Lung's eyes fixed on the new heroine, then narrowed.



``\emph{I admitted to reprehensible things.  I won't challenge that, or pretend I didn't say or do those things.  By all rights, I should go to jail.  I may serve a sentence, if the courts will it.  I won't challenge that.}''



``is it reassuring?'' Teacher murmured.



Lung turned, realizing that Teacher was talking to him.  ``Why would it be?''



``You lost to her, but she's strong enough to defeat Alexandria.  Less of a wound to your ego?''



``I lost once,'' Lung said.  ``An underhanded trick, but a loss.  I'll credit her that.''



``Mm hmm,'' Teacher replied, wordlessly.



The girl continued, ``\emph{I seized a territory in Brockton Bay.  I led the local villains, and we defeated all comers.  I was secure in my position.  I had wealth, friendship, love and respect.  People depended on me.  It was everything I'd ever wanted, if not quite the way I'd initially imagined it.  I could have stayed and been comfortable. Except there are bigger things.  More important things.}''



``She was stronger before,'' Lung spoke his thoughts aloud.



``More powerful?  Likely,'' Teacher said.  ``Stronger?  I wonder.''



Lung shook his head.



``\emph{I believe in the idea of a new PRT that Chevalier is talking about.  I believe in it enough that I was willing to turn myself in and take action to bring it to fruition.  That I was willing to leave everything I had behind.  If I have to serve time in jail first, then so be it.  If I face the Birdcage\ldots I hope I don't.  But at least I could tell myself that seeing the supervillain step up might convince others to come back.  Change the minds of heroes who gave up on the PRT for one reason or another.}''



``Noble,'' Marquis said.  ``Foolish at the same time, but the line between the noble and the fool is a thin one, or even a matter of perspective.''



``On this, we may agree,'' Lung rumbled.



``I'll endeavor to see that as something other than a veiled insult,'' Marquis said.



``\emph{This is what I want to do, above all else.  Given the chance, I'll serve the people.  As I fought Leviathan, the Slaughterhouse Nine and other evils, I'll fight to the last gasp to protect all of you.  When-  \ldotsWhen and if I do take up the job, you can call me Weaver.}''



The broadcast ended, with news reporters discussing the fallout, reiterating details.



The noise of it was broken down by singing, echoing through the Birdcage.  A dirge.



\emph{The yellow feathered girl who was in the truck, }Lung thought to himself.



``That's for Alexandria, I imagine,'' Marquis said aloud.  ``Undeserved, I think, but I imagine Lustrum gave her cell block a very good reason to honor the woman.''



``I wouldn't have imagined you'd care,'' Teacher commented.



``I don't, really,'' Marquis answered.  ``But I have a lot of respect for people who keep to a particular code, whatever that code might be, and very little for traitors and wafflers.



``Like this new `Weaver'?'' Teacher asked.



``I would defer to my daughter's opinion on that.  She knew Weaver.''



Amelia frowned.  ``She's\ldots both?  She's stuck to her own personal code, even when it made her a traitor.''



``I see,'' Marquis mused, rubbing his chin.



Lung frowned.  All nonsense, and none of it mattered.  That was out there, this was here.



``A word, Lung?'' Teacher asked.



Lung nodded.  Anything to get away from this intolerable talk of morality and \emph{this singing}.  His cell wouldn't afford much relief, but it would be a touch quieter.



They departed, but Teacher led the way out of Marquis' cell block, rather than to Lung's cell.



``I believe I can be useful to you,'' Teacher said.



``You have nothing to give me,'' Lung said.  He bristled at the implication.



``You know how my power works, yes?''



``You make others smarter.''



``I turn others into lesser Thinkers, into Tinkers.''



``At the cost of their independence.''



``Yes.''



``Not something I want,'' Lung said.



``You have strength, good instincts on a primal level, and all the potential in the world.  Yet you've failed here and there.  You're \emph{here}, after all.''



``And so are you,'' Lung said.



Teacher nodded.  ``Exactly my point.  Think on that for a moment.  We're almost to my cell block, now.''



``You were captured because you lacked muscle,'' Lung said, ``I was captured because\ldots''



Lung didn't like the implication.  \emph{Of a lack of brains?}



``Because of your incompetent underlings,'' Teacher finished for him.  ``Who escalated the feud with the heroes into a war while you were incarcerated, leaving you to sustain what they had started.  And, more apropos to our conversation, because your power has a drawback.  It requires a certain mental state.''



``Yes.''



``Amelia, Marquis' girl, she won't fix that.''



``I wouldn't let her,'' Lung said.



``Because it involves tampering with your brain,'' Teacher said.  ``My offer is\ldots less invasive.  We can break down that barrier, give you the ability to control when you change.''



``At the cost of my identity,'' Lung said.  ``No.''



``A \emph{temporary} cost to your willpower,'' Teacher said.  He extended a hand, welcoming Lung into his cell block.



There was no conversation in Teacher's cell block.  The residents were neat, tidy, and well groomed.  Some seemed functional, reading on their own or watching television.  Others were more disabled.  Lung could see one individual rocking in place, tapping something out on a table.  Another was walking in small, tight circles.



``My groupthink,'' Teacher said.  ``Rest assured, I wouldn't subject you to something this grave.  We would dig deep enough to discover the true nature of your power, fast enough that you didn't feel the side effects at their worst.  Then we would use what is effectively a hypnotic state to unlock your power as it truly should be, effectively a second trigger event.  If Amelia is right, the entity that grants you your power will resist\ldots but we can get around that.''



Lung frowned.  ``There is no point.''



``There is \emph{every} point!  Come.  I'll show you.  But first you need to tell me, are you and Marquis friends?''



Lung shook his head.



``Peers, then.''



Lung considered the word.  There were some that came up in English that he still wasn't quite familiar with.  ``Yes.''



``Then you'll keep a secret?'' Teacher asked.



``I will keep a secret,'' Lung answered.



``Good, good.''  Teacher led Lung to one TV in the row.  ``Trickster?''



Lung arched an eyebrow.  Trickster\ldots the name rung a bell.  It didn't matter.



``Connect,'' Teacher said.



Trickster reached up to the power button on the television, then began a sequence of turning it on and off, with very specific pauses.  A code.



The sequence was still going on when Teacher said, ``Stop.  Leave it on.''



The screen showed a face, the image grainy, flickering.  The face had a tattoo of a cross on it.



``Lung, meet Saint,'' Teacher said.



Lung didn't answer.



``He speaks when we give him something to say,'' Teacher said.  ``But I may have been too eager to find a way of contacting the outside world, and I've irritated him.  Saint explained what happened.  The PRT showed him Dragon's equipment, asked if he could commandeer it, and Saint found an opportunity to insert a discreet backdoor.  He has a channel in, a way to observe, but our channel \emph{out} is poor at best.''



``This matters nothing to me.''



``It matters a great deal,'' Teacher said.  ``Saint can see what Dragon sees, even if he's blocked off from the Birdcage itself, while Dragon is occupied elsewhere.  It buys us a window of opportunity to communicate something, a message in code.  The program that Dragon has observing us with every moment tracks the activity of our televisions.  Turn it on, turn it off, and do it in a systematic enough way, and patterns emerge in a way that Saint can observe.  This allows us to \emph{coordinate}.  He can't rescue us, or empty the Birdcage, but, we could do \emph{something}.  We could communicate with the outside world, and with the hypothesis that Amelia has posed\ldots well, that's a world changing set of information, don't you imagine?''



Lung didn't speak.



``The alternative, Lung, is that we unlock your power, and we use \emph{other} information that Saint has collected through his backdoor.  We use it to leave the Birdcage.''



``To escape?''



Teacher shook his head.  ``We wait, and we let things devolve to the point that they are willing to open the door and let us go, for the assistance we can give.  Dragon has files dictating scenarios in that vein.''



``They will not let us go free,'' Lung said.  ``Not the true monsters.''



``Most likely not.  It's a question: do we gamble, or do we take a modicum of comfort in knowing we've perhaps saved the world a great deal of grief and maintained the status quo?  The way things are, if you're not familiar with that particular phrase.''



Lung folded his arms.  ``I have no attachment to the current state of things.''



``Then you agree?  I should tell Saint to bury the information, maybe push events here and there, if it means we could go free?''



Lung nodded.



``And your power?  If I-''



``My power will be left alone,'' Lung said.  ``It is enough.  If you want a bodyguard for a time after we've walked free, you will have it.  I will keep your secret about this Saint for now.''



``Alas,'' Teacher said.  ``But I'll take the offer.  By the time this comes through, I'll have a small army of parahumans at my disposal.  Some will be\ldots under my sway, but I'd rather have your feral instincts to offset my own wit than have you as a slave.''



``I would kill you for trying,'' Lung replied.  ``You use your power on me, I will see you dead for it.''



``Very well,'' Teacher answered.  He smiled.  ``I'll have Trickster pass on a message to Saint, then.  We'll scrub Dragon's records of this conversation, and any cases Amelia has talked of the power-granting entities, and we'll leave a request, perhaps.  I have large sums of money stashed away.  That should be enough to convince Saint to perhaps set some events in motion, in the hopes that things sour just enough that they might open the Birdcage's doors.''



Lung nodded.  ``Do what you must.  I only care for our deal.  I walk free, I will assist you for a time thereafter.  The other things do not matter to me.''



``Very well.''  Teacher extended a hand, and Lung shook it.



Lung turned to leave.



As with the Y\`{a}ngb\v{a}n, he would stay with Teacher until he had what he needed: freedom.  Then the man would die.



The woman in the black suit, the Y\`{a}ngb\v{a}n, Skitter, and now Teacher.  People he would have his revenge on, at a later date.  People who had looked down on him, who had tried to manipulate him.



He could feel his power rippling under his skin.  Against Leviathan, he'd waited hours before engaging the beast, had fought longer than he ever had.  Now that he knew he might leave\ldots this would be a two year buildup.



The scale of the event Teacher had spoken of?  That Amelia had alluded to?  Fear and power beyond anything he'd ever experienced, freedom without limits.  That very idea gave Lung a taste of that exhiliration he hadn't experienced for so long.



Lung returned to Marquis' cell block.  Marquis and Amelia were sitting at one table, drinking green tea and conversing with one another.



Marquis glanced at Lung, then poured out another mug of green tea without asking.  He gestured to the bench opposite, slid the mug in Lung's direction.



\emph{Acceptance}, the idea caught Lung by surprise.  He had a place here, odd as it was, as different as he and Marquis were.



Bakuda had taunted him over how he'd sought a kind of connection to others, how he'd recruited his gang to fill a void.  At the same time he found himself thinking of the restrictions he'd faced in school as a youth, the joys of rebellion, the Y\`{a}ngb\v{a}n and everything they'd threatened to take from him.



If there was a middle ground between acceptance and conformity, was this it?



``Marquis,'' Lung spoke, carefully.



``Hm?'' Marquis quirked an eyebrow.



\emph{Teacher is working to undermine everything you and your daughter are striving for}, Lung thought.



``The tea is good.  Thank you.''



``Quite welcome,'' Marquis replied, absently.



And Lung fell silent.





