





It was seven-thirty in the evening in a medium sized airport.  Weren't there supposed to be people?



There had been staff, for sure.  The odd staff member to greet him as he got off the plane, another to see him past the gates.  Still, the terminals were empty, there were no crowds, the shops and restaurants were all closed.  Only half the lights were on.  For the first time, he was wondering if he was getting in over his head.



At least there were no people making the same old jokes about the metal detectors.



Baggage claim had three carousels, which should have been in operation, delivering a regular supply of people's luggage onto the conveyor belts, crowds gathered around them in anticipation.  Instead, there was a single man in uniform with three large bags already piled onto a cart.



``I can take my bags, I'm stronger than I look.''



``It's alright, son,'' the man replied, ``It's good to have something to do that isn't cleaning up.''



\emph{Son}.  That bothered him more than he cared to admit.  Not that he had any ideas about his own ethnicity, but it was vaguely condescending.  A reminder that people didn't know how to act around him.



``Alright,'' he conceded, ``Where are we headed?''



The man gestured toward a set of double doors, then gripped the handle of the cart to push it in that same direction.



Stainless steel handles on the doors.  He put his hands on the painted surface instead, pushed them open, and then held one of the doors open for the cart.  He was distracted enough that he almost didn't notice the group waiting for him.



The group consisted of a squad of PRT officers with their regular assortment of nonlethal weaponry and a large woman with a bleached blonde bob.



``Weld, I'm glad you made it,'' she managed to say the words without a trace of humor or smile on her face.  She extended a hand.



He glanced quickly at her hand, checking there were no rings, then shook it.  ``Thank you, ma'am.  Director Piggot, I'm assuming?''



``You assume correctly.  Shall we?''



He nodded.



As they fell into step, he asked, ``Where is everyone?''



``This airport was attacked by one of the local villain groups just three days ago.  The front lobby and ticket claim were ransacked, and the airport has shut down for the time being, with only special cases such as yourself coming or going.''



``I take it things are bad?''



``Yes.  We have seen this type of situation before, if not to this extreme.  Too many citizens here had been living paycheck to paycheck or were unemployed.  There was a great deal of latent frustration and unhappiness with the status quo.  A powder keg needing only a spark to set it off.''



Weld nodded, ``And the arrival of an Endbringer is a bit more than a spark.  I see.  I know the Endbringers tend to target areas where they know they can do the most damage.  You think Leviathan did it on purpose?  Attacked this city because he knew this would happen?''



``If someone raised the idea, I wouldn't dismiss it.  But our focus should be on what we do in the here and now.  Are you ready to take command of the local Wards?''



``I'm ready to try.''



``Good.  The team here is smaller than your old team in Boston.  It currently consists of Clockblocker, Vista, Kid Win and Shadow Stalker.  We had two members die in the attack, and a third left with his family when they evacuated.''



PRT uniforms opened the doors, and he followed the Director onto a helipad, followed shortly after by the other PRT uniforms and man with his luggage.  A black helicopter with the PRT logo on the sides sat there, propeller already whirring in preparation for takeoff.



The Director took the hand of a uniform inside the helicopter, stepping inside, and Weld followed her up, refusing a helping hand.  The helicopter shifted slightly with the addition of his six hundred pounds of weight.



When the door shut, cutting off the worst of the noise, he took the offered headphones and put them on.  When he spoke, his voice came through the headphones crystal clear, without a trace of the ambient noise of the helicopter, ``So there's only five of us?''



``There will be more.  We've got a lead on a young man who could be joining as a new member, assuming we can get close enough to him to make the offer.  I trust you know your classifications?''



``I do,'' Weld nodded.  He'd memorized it as a rhyme, as suggested by his old boss.  Maybe that had been the intention from the start:



Mover, Shaker,
Brute and Breaker.



Master, Tinker,
Blaster and Thinker, 



Striker, Changer,
Trump and Stranger. 



He was classified as a brute and changer, classifications meant for the unnaturally tough and strong and for those who could change their shape to some extent, respectively.  He never liked the word brute being applied to him, even though he was aware that the labels had originally been intended for the PRT teams to identify and label villains, specifically.  It was only later that they had been extended to identifying the heroes as well.



``Right.  This potential recruit is tentatively marked down as a Tinker/Mover.  It isn't unusual for powers to emerge in the wake of an event as serious as this.  For this reason, we keep careful track of things to see if we cannot detect any new parahumans.  This young man has been observed in the south end, moving at over a hundred miles an hour with the assistance of a mechanical suit.  His inclusion on a local team would help fill gaps left by the death of Velocity, a local Protectorate member, and Armsmaster's retirement.''



Weld nodded.



``Others may make themselves known, and we will approach each of them in turn.  To help fill the gap in the meantime, Flechette is arriving from New York.''



Weld chuckled, just under his breath.



``Something amusing?''



He was surprised that she had heard or noticed the laugh.  ``No, it's just that we know each other.  Our teams are -were- friendly rivals, kind of.  We'd meet two or three times a year and compete, just to spar and practice our skills against less familiar opponents.  We'd joke around about which team was better, give each other a hard time.''



``I certainly hope this `rivalry' isn't going to hamper your ability to lead this team and work with her.''  There was no humor in her tone.  Just the opposite.



``Um, no, ma'am,'' he replied, chastened.  The helicopter lifted into the air.  A glance out the window showed the sprawl of the city.  It was dark out, but much of the city was unlit, nothing shining through the windows, no street lights illuminating the roads, nor the headlights and taillights of traffic.



Noting where he was looking, Director Piggot spoke, ``Because the current situation \emph{is} serious, and it isn't improving as fast as we'd like.  You're going to have to be on the top of your game.''



``Yes ma'am.''



``Clockblocker and Vista are your best assets.  Clockblocker is a Striker 7 with touch-based time-stopping.  Vista is a Shaker 9.  Large scale spatial distortion.''



``Geez louise.  The others?''



``Kid Win is a Tinker 4.  Guns and antigravity devices, primarily.  Shadow Stalker is more ambiguous.  Breaker 3, sublabels are Stranger 2, Mover 1.  Her particular nature as a `breaker' makes her superlight, semi-gaseous, transparent and capable of passing through solid surfaces.''



``Okay.  The team sounds well rounded, I can work with that.''



She handed him a stack of files, ``Here's the files on local factions, including your new team, and a file on the solo heroes and villains.  You'll have limited access to the databases as well, which you should be familiar with, but this should get you the essential details to get underway.  I've ordered those files loosely by priority, so you'll find the most need-to-know information at the top of the pile.''



Weld took the folders and opened the one for the Wards, glanced through it to memorize the faces of his new team.  Then he went to the next file, ``Then the top priority as far as opposition goes is\ldots the Archer's Bridge Merchants?  Superpowered drug dealers.  A Shaker 2, Tinker 2/Mover 3 and a Shifter 4.  These aren't big numbers.  Am I missing something?''



``Context.  They've become a rallying point, representatives and leaders for those on the lowest rungs of society.  Too many civilians who were the have-nots think allying with the Merchants is a way to become the haves.  People that were angry, disenfranchised or both have gravitated towards the group, are seeking to overturn the social order.''



``So they've got, what, a following of homeless?''



``Brockton Bay doesn't, or didn't,  have many that you could strictly call homeless, as there were so many abandoned buildings to squat in.  When the Endbringer attacked, he chose the area with many of these buildings.''



``I think I remember, yeah.  The area where the fight started didn't exactly look upscale.''



``The sad irony of this is that the defending parahumans protected that area, while other locations were leveled by the tidal waves.  That area, known to locals as the Docks, was not under the control of any organized crime or villain organization even before the attack.  After the battle's conclusion, it was swiftly occupied by the Merchants and growing numbers of their followers, and is now one of the areas with reliable shelter.  Not entirely, but more than many.  By the time our local heroes were finished with search, rescue and minimizing damage, their number of followers had reached a critical mass.  In the past several days, they've begun attacking the city infrastructure, the airport, grocery stores, malls and they've repeatedly seized medical supplies and food as they come in.''



``So a big priority will be safeguarding incoming supplies from relief efforts, protecting key areas of the city so it can recuperate from the disaster.''



``Yes, for the time being.''



``Let's see, the next group is\ldots Fenrir's Chosen?''



``One of two major offshoots of the Aryan villain group, Empire Eighty-Eight, which fell apart after the death of their leader, Kaiser.  Fenrir's Chosen are led by Hookwolf.  Violent, utterly merciless, and reveling in the current chaos.''



``And it looks like he's a Shaper 4, Brute 7, with the longest list of homicides or suspected homicides I've seen on someone who wasn't already in prison.  Thick file, I take it he has lots of followers?''



``The largest group in terms of parahuman numbers, at present.''



``And this second group, The Pure, is the second offshoot of that Aryan group, I take it?''



``Small but powerful.  Their leader, Purity, is a Blaster 8 and Mover 4.''



``Yeah, there's a Breaker 9, a Shifter 8 with Stranger 3 and a Master 6 in that group?  I buy that they're powerful.''



``Their leader has made overtures to us, offering cooperation in helping us regain control of the city.  We have refused her for the time being.  If she approaches you, you are in no way, shape or form permitted to agree to any deals.''



``Noted.  Let's see\ldots  Coil, powers unknown.  The Travelers have high ratings on their powers, but their crimes are low end, pretty much.  There's the Undersiders\ldots three Master classifications in one team.''



``Only one of whom is of any particular concern.  Investigations into two members have suggested sociopathic tendencies, and if they're channeling their efforts into low threat activities such as robberies, we can afford to ignore them for the time being.''



``Faultline's Crew.  Mercenaries, low rating, mediocre rating, low rating\ldots  A Shaker 12?  Seriously?''



``The girl has cognitive deficiencies that reduce the effective threat she poses, but yes.  Again, that group is not an imminent threat.  In the current situation, I might suggest you leave them be if you cross paths, conserve your group's strength for the priority opponents.  The Merchants and Hookwolf's group.''



``Okay.  I'll have this memorized by the end of the week.''



``I expect you will.  That brings us to more mundane matters.  You'll be enrolled full-time at Arcadia High School.  It's close to the Wards headquarters, and your teachers have been informed about your special nature.  I'm afraid there's no easy answers as far as your appearance and how the rest of the student body will react to you.''



Weld looked down at his hands.  His body, from skin to hair to bone, was all metal and alloys of varying types.  ``I've dealt with it before, I'll manage.''



``We can't enroll you in the co-op program, as your absence would be noted, and would draw attention to others who are using the co-op program to mask their attendance in the Wards.  It won't be easy, attending high school full-time, keeping up with your coursework and leading the team in your off hours.''



``It's fine.  I don't have to sleep much, anyways, so it's good to keep busy.''



``Good to hear that.  All that said, I have asked your teachers to make special arrangements, reducing expectations toward your homework, provided you are not struggling in any subjects.  The Wards program will also provide tutors should you need them.''



``Okay, cool.''



``You'll have time to get into the swing of things without worrying about school, as the high schools are all currently shut down for repairs and to allow time for thorough investigation of the premises.  When the schools are open, we'll have you take three courses and attend first year classes on parahumans at the University, if that suits you?''



``Perfect.''



``You'll be living in a private room in the Wards headquarters, and you'll have a monthly allowance of four hundred dollars in addition to the money put into your trust account by the program.  We expect you'll spend this allowance on necessities, such as food and clothing.  You do still eat, yes?''



``Yes,'' he answered her, bending the truth.  While he did eat, it was a negligible amount.  As he saw it, there was no real harm done if he pocketed some of that extra money and said he spent it on food.  Given that his tongue was made of an alloy and the pleasures of food were a shadow of what they should be, it was only fair that he enjoy himself in some other way.  He knew that some staff back in Boston had caught on, but they hadn't said anything.  Director Piggot here gave him the vibe that maybe she wouldn't be so cool with it.  He'd be more careful until he knew for sure.



``Your quarters have been checked and double checked, so there is no exposed metal, no screws, nails, frames or pegs.''



``I appreciate the thought,'' he told her.  His physiology had the unfortunate drawback that he couldn't help but attach to and absorb metal he touched.  While it had been crippling when he'd first been found, dumped in a junkyard, he had learned ways around it.  He could rearrange the metals that formed his body, separate them into their composite elements, and he extended this particular trick to push all the impurities in the metals out to his `skin'.  The impurities, unlike the metal that composed the rest of him, didn't bond, giving him the ability to handle things with his hands and teeth if he needed to.  It didn't always work – at least once a week there was one embarrassing moments where he bonded with someone's wedding ring during a handshake or bumped into a shelf display – but it helped.  Clothes helped as well.



In a more serious situation, such as when he was out on patrol, he could force parts of himself to melt and drop off, leaving a piece of himself behind, but it made him distinctly uncomfortable – pain wasn't the right word – until he replaced the tissue he'd lost.  More often, he preferred to just tear the offending piece of metal from whatever surface it rested on, whether it was a segment of chain link fence or a hubcap.  Whenever he did it, he'd have to spend as much as an hour dissolving the metal and absorbing it into his body.  Either way, they were only emergency measures.



Which wasn't to say he was weak.  Being made of materials and alloys as strong or stronger than steel from head to toe made him practically untouchable in a fight.  In addition, his biology fell into some optimal middle ground between organic and inorganic.  For those whose powers affected only living things, he counted as inorganic.  The opposite was also true.



``Do you understand why we have gone to this trouble for your sake, Weld?  Why we are testing your ability as a team leader in a crisis such as this?''



``You're grooming me,'' he replied.



``Yes, but do you understand \emph{what} we're grooming you for?'' she pressed.



He knew, but he assumed she would prefer to explain.  Besides, \emph{how} she explained would inform him a great deal about his new boss's personality.  ``Not really.''



``You likely know Director Armstrong in Boston, how he tends to prioritize research and understanding parahumans.  I concern myself with more concrete affairs.  Public relations, parahumans as a part of America.''



Weld nodded.



``What Armstrong continually fails to grasp is that if we do not integrate parahumans into society, help society bend to accommodate your kind, there is no point in lab experiments or classifications.  As bad as things might be with the periodic arrival of Endbringers and parahuman criminals, matters could be ten times worse if panic or prejudice takes hold from the public.  You understand?''



``One thing, ma'am,'' Weld spoke.



``Yes?''



He took a deep breath.  Not that he really needed it, but he did anyways.  ``Forgive me for saying so, but I get the impression you don't like or respect Director Armstrong?''



``Your point?''



``I just thought you should know he's something like a father figure to me.  He's the one who recruited me to the Wards, got me up to speed.  I've already made plans to go to his house for a bit this summer.  Maybe I'm putting myself on your sh\ldots in your bad books by saying so, but I just thought I should let you know I'll step up to defend him if you start putting him down.''



``I see,'' tiny frown lines appeared between her eyebrows.



``Sorry.''



A fire on a street below caught his attention.  A car had been set on fire, and people were crowding around it.



Not noticing, Piggot pursed her lips, ``Fine.  My apologies for putting you in that situation.  I won't say anything further about Director Armstrong for the time being.  I was speaking of the need for public relations?''



``Yes ma'am,'' he spoke, feeling somewhat relieved at her composure.  He wouldn't feel a hundred percent okay about it until he verified her as someone who wouldn't find some other way to get back at him.



``As the number of parahumans first became clear, a long-term plan was established.  In the early phases of the plan, much effort was dedicated to setting up the Protectorate and Wards, ensuring the public had heroes they could look up to, likable faces, likable personalities.  Merchandising, interviews, tv shows, music, movies and more were all encouraged and supported with the idea of building up this image.  Law, policy and rules for the official groups were all shaped with the idea of gradually building confidence in heroes.''



Weld nodded.



``As we enter the next phase, our objective is to push the public a margin beyond their comfort zone.  We are encouraging and promoting the existence of rogues, which is an unfortunate term that heralds back to the early days.''



``Right,'' Weld responded.  The term `rogue' applied to anyone with powers who wasn't hero or villain, the negative connotations of the term tying back to an era when expectations had been rather different, much the same way the brute classification had been coined.



``This is a sensitive subject, slow to advance, as major corporations are particularly litigious when parahumans get involved.  In simple terms, the big businesses do not want people with powers affecting the status quo, and it is \emph{very} easy for them to derail years of work with one bad media campaign targeting parahumans.''



``I see,'' Weld commented.  He didn't like that \emph{in simple terms} bit of what she'd said.  Too many people implied he was stupid because he was strong.  But could he really speak up about it, when he couldn't be sure if her choice of words came from an offensive or judgemental perspective?  Or was he being overly sensitive?



``The second half of this phase is getting the public more comfortable with the outliers.  The people with stranger powers, and stranger appearances.  You're likable, Weld.  You have a clearly unnatural appearance, if you'll forgive me saying so-''



Weld shrugged.  He stood out.  There were a hundred things that bothered him more than stares and comments on the subject.



``-but you have fans, and people are interested in you.  You get higher ratings for your interviews than even the average handsome hero gets.  You're second most popular for team leaders for number of youtube videos, possibly helped by a briefly lived internet meme featuring your face, and you have a blemish-free record, both academically and in your two years serving as a part of the Wards.''



``Thank you.''



``Provided all goes according to plan, we intend for you to become a member of the core Protectorate team within the span of three to five years.  Making your face national, even international,\emph{ if} you are willing.''



``Wow.  Yeah, I'm definitely okay with that, ma'am,'' he tried to feign surprise.  Armstrong had already covered much of this.



``Of course, this hinges on your ability to lead your team, in the here and now.''



``Of course.''



``It seems we will land shortly.  Any questions before we do?''



``One.  I was hoping to arrange interstate training sessions with the New York and Boston Wards groups.  As far as I'm aware, the local team doesn't do this.  They barely have regular situation training.''



``I recall Triumph made a request for something like this, a few years ago.  I believe we refused him on the grounds that it was frivolous.''



Weld squared his shoulders.  He had to be assertive, here. ``I'm firmly of the opinion that it would improve the local team's ability to cooperate and respond to a greater variety of situations.  I'm totally prepared to eat any and all paperwork on our end.''



``\emph{Eat} the paperwork?''



``I mean I'll do it all, for the members of my team.  Give you updates after any and all training sessions.  Notes on improvements, lessons learned, weak areas, strengths, resources that could fill any perceived gaps.''



``So long as you're prepared for me to put a stop to things at any time.''



``Yes, ma'am.''



``And,'' the Director paused a moment as the Helicopter touched down on solid ground, ``It cannot cut into the regular patrol schedule.  You and your team members would do this outside of the hours you're on clock for the Wards.''



``I'll see if I can sell it to them.  Thank you, Director,'' Weld stood.



Secretly, he was elated.  The training games he'd led his team through back in Boston had been some of the more fun moments of his career.  It had also allowed for a harmless but fun interaction with the New York group, giving them a chance to mingle, talk and share war stories.  There was something about being able to mess with others on a level that you couldn't with teammates you had to fight alongside.  If his new team liked the games half as much as he did, it would be a win in his book.



``Do you wish me to come down and introduce you?''



That earned a moment's consideration.  Was this woman likable?  No.  Would the others like her?  Probably not.  Which meant that having her introduce him might be detrimental, associate him with someone they might view negatively.



``No, I don't think it's necessary, ma'am.''



``Your old keycards will let you in.  I'll have replacement identification sent to you shortly.  In the meantime, I wish you luck.''



``Thank you, Director,'' he handed her his headset and stepped through the door as PRT uniforms opened it.  As if welcoming him into the city proper, there was the sound of a woman screaming down on the street below, the noise turning into a manic laugh in the same breath.  Half the block was without power, and searchlights on the corners of the rooftop scanned nearby streets.  PRT guards stood at the edge of the roof, armaments in hand.  He relaxed at the sight of the guards – if they weren't acting on whatever was going on below, he didn't need to worry about it.



He took a deep breath, deep enough that he could feel the groan of the metal stretching to its limits inside his chest.  Then he stepped off the rooftop and through the elevator doors.  When the complex chrome doors shut, they cut off the noise of the helicopter entirely.



It was utterly quiet, inside the box.  There was barely any sense of motion or movement from the elevator.  Tinker designed.  It had to be.  He avoided touching the chrome walls or railing.  It was probably coated with something, but emerging with a piece of railing stuck to him would make for a terrible first impression.



Stepping out into a hallway, he walked up to a security terminal.  He swiped his identification card, spoke his name for the voice authentication, ``Weld.''  There was a pause, and then the doors glided open.



His team was there, each with their masks off.



Clockblocker sat in a chair at the huge computer to the right of the room, swiveled to check out their new arrival, then stood, folding his arms.  Red haired, freckled, thin lipped, he wore a costume that was all white, with animated images of clock faces on it.  A white helmet sat on the counter of the computer terminal.



Shadow Stalker was leaning against a wall, thumbing through a smartphone.  She had one foot against the wall, one arm folded just under her chest, her free hand resting in the crook of her other elbow.  She looked up at him, stuck the phone in a pouch on her belt.  She was dark-skinned, pretty, and from  what he could see beneath her costume and her voluminous cloak, she had a nice body.  Athletic figure.  A part of Weld's adolescent psyche was relieved that there was some eye candy here.



Kid Win and Vista arrived from what the `cubicles' at the far end of the spacious room.  They weren't really cubicles, but sectioned off areas with beds and room for personal effects.  The base in Boston had been similar.  Kid Win was in civilian clothes, brown-haired, ruddy cheeked in a way that suggested he had been exercising until just recently.  Very normal looking.



Vista was in pyjamas, her hair tied back into a ponytail.  He'd had someone as young as her on his team in Boston, but the boy had been a Thinker, a limited precog content to work and communicate with them from their command station.  This girl had been out in the field – three fingers on her left hand were bandaged, with crimson seeping in through the white.  Her eyes were puffy, as though she'd been crying until very recently.



Should he comment on that?  Offer support?  He wasn't sure what to say, if it would even be welcome.



``Hello,'' he spoke.  He received a chorus of muttered and murmured greetings in return.



``Look,'' he said, ``I won't make a big deal of this.  The guys upstairs want me in charge.  It's going to take me a short while to get up to speed, but I hope to prove to you guys that I can and will work as hard as anyone.''



It was hard to say what he'd expected, but surely he should have gotten more of a response than some blank stares and glazed looks.  Was it the wrong time for this?  Every single one of them looked dog tired.  Clockblocker looked like he was barely managing to stand.



``From everything I've heard, you guys are an excellent team, and I hope I can do you justice as a leader.  It's my hope that we can improve on a winning formula.  I've talked to the director about some special training-''



``Training?'' Clockblocker interrupted, ``You just lost me.''



``If you'll hear me out, I think you'll like the idea.''



``Have you seen the situation out there?'' Clockblocker challenged him, ``Less than an hour ago, I saved a guy I know from my high school physics class from being dragged into an alley by a half-dozen grown men.  One of them stuck him with a needle before I got him away from them.  The Hospitals are shut down or over capacity, so I brought him here.  He's upstairs right now, getting drugs to ensure he doesn't get HIV.''



Weld struggled to find something to say, failed.



Clockblocker went on, ``Kid Win and I stopped some lunatics in gas masks from mixing ammonia and bleach into a poison gas.  You know why?  They wanted to off the people in an apartment block so they could loot the place and stay there.  There's people going fucking crazy out there, and you're talking \emph{training}.''



``I didn't mean now,'' Weld protested, backpedaling, ``I was thinking in terms of the future.  The training would be something to look forward to, after this crisis has passed.''



``You're assuming it's going to pass,'' Shadow Stalker replied, her voice tired.  ``Some are saying this is the way things are going to stay.  I almost agree with them.  This isn't the kind of city that bounces back from things.''



\emph{I'm losing them}.  ``I can't believe that.  We've got to have hope.''



``Pull a fifteen hour patrol out there, then come back and talk to me about hope,'' Clockblocker spoke.  ``You know, I could almost play along.  Go with the blind optimism, say yippee to training.  But you don't even mention the guy you're replacing?  A few words for the dead?  It's a matter of respect, bro.''



``I didn't mean to dismiss them or their sacrifice.  I just didn't know them, and-''



Clockblocker turned, swiping his arm angrily at his helmet to snatch it off the counter.  Tucking it under one arm, he spoke to the others, his back to Weld, ``I'm going to check on my family.  I'll head there in costume, in case I run into trouble, be back in the morning.  Mind manning the console, Kid?''



Kid Win shook his head, ``I need to take a break anyways.''



Vista glanced at Weld, then asked, ``Where do you guys need me?''



``Go sleep,'' Shadow Stalker spoke, placing a hand on Vista's head as she walked past the girl, ``I'll start my patrol, go with Clock to make sure he gets home and that he has some backup.  You can relieve me when I'm back, maybe get Clockblocker to go with you.''



``Thank you,'' Vista's voice piped up, with a definite note of relief.



Helplessly, Weld watched as the team split up to go their separate ways, Kid Win sitting down at the far end of the computer station, Shadow Stalker and Clockblocker heading for the elevator.



``I fucked up.  I already lost them,'' Weld spoke, mostly to himself.



``No.  They're just tired,'' Vista spoke from beside him.  ``And not just lack of sleep.  You'll see what I mean.  You could've mentioned Aegis and Gallant, but you can't be blamed if Clockblocker didn't give you time to get around to it.  Nobody's really in the mood for speeches.''



``Right,'' Weld replied, feeling lost, ``Aegis and Gallant.  They're the ones who died?''



Vista gave him a look that could only be described as pity.  ``You didn't even learn their names?  Nevermind what I just said.  Yeah, you fucked up.''



Then she turned away and walked back to the cubicles.  She was halfway there when he saw her rub at one cheek with the back of her hand.



``I\ldots I just got here,'' Weld said, helplessly.



\emph{I just got told by a pre-teen}, he thought.



``Shit,'' he swore under his breath.  He found a chair in front of the computer and dropped the stack of file folders on the nearest flat surface.  He plucked the file folder off the top of the stack, opened it and began studying.





