





Flechette spoke, ``You're a hard person to fin--''



Shadow Stalker, transparent and wispy, whirled on the spot, not even pausing as she fired her crossbows.  The first bolt went wide.  Flechette caught the second out of the air, staggered back a step as she was caught off balance.  Her right foot skidded to the edge of the rooftop.



``What the hell!?''



Shadow Stalker rose from a crouch, becoming opaque in the process, ``Oh.  You shouldn't sneak up on people when they're on patrol.''



\emph{What}?  \emph{I nearly get shot and she blames me}?



``You nearly killed me!''



``It's a tranquilizer shot, and you have the fire escape behind you.''



Flechette turned to see Shadow Stalker was right about the fire escape.  The bolt in her hand had a glass shaft, filled with fluid, a three-pronged head with a wider cross-shaped flare at the base of it to prevent it from stabbing too deep.  Tinker made?  ``Geez.  You shaved a year off my life, doing that.''



``Sorry.  A little twitchy.  Good to see you,''  Shadow Stalker crossed the roof, offered a hand.  Flechette shook it.



``I suppose being twitchy is excusable,'' Flechette excused Shadow Stalker, looking out beyond the rooftop to the dark streets.  Some of the buildings looked ready to fall over, and the main street below the pair had a two-foot crack running down the middle.  Water covered everything at the ground level, a half-foot deep.  ``And the apology is accepted.''



``So.  You joining the team?''



``No.  Temporary stay, until you guys fill out your ranks again.  Maybe a few weeks, maybe as much as a month or two.  Weld told me you were out on patrol, that you might need backup.''



``I don't do backup, and I don't do the team thing unless someone makes me, but I'm willing to hang with another crossbow aficionado.  Is that the right word?  Aficionado?''



Flechette smiled, ``It is.  The brown haired guy at the computer told me you'd be around here.  Took me almost two hours to spot you, though I did get sidetracked by some kids taking clothing from a broken display window.  We'll patrol?''



``Sure,'' Shadow Stalker agreed, lowering her eyes to her crossbows as she picked bolts out of one of the three cartridges mounted on her forearm and loaded them into her crossbows.  ``You look like a rooftop type.  Fly?  Glide?  Grappling hook?''



``Grappling hook,'' she patted her weapon, touched the chain that ran along her arm to the automatic-firing crossbow, her arbalest.



``If you can't keep up, don't worry about it.  Keep moving in a straight line, I'm mostly untouchable, hard to spot, so I'll scout ahead for trouble, double back every minute or so to check on you.''



``Got it.''



Shadow Stalker swept her cloak over one shoulder, simultaneously shifting into her shadow state.  She turned and leaped twenty feet to the side of a neighboring building.  Grabbing a windowsill, she vaulted herself another fifteen or so feet straight up the face of the building, caught another windowsill, and then heaved herself up once more to reach the rooftop.  Her cloak billowed out around her, and Flechette saw how Shadow Stalker's costume clung to her body.  One of the surprisingly few people who could wear a skintight costume without armor pads or features to mask minor physical imperfections and emphasize or suggest certain features.



When Shadow Stalker had disappeared from view, Flechette remembered she was supposed to follow.  She cocked her arbalest, flipped a switch beneath the trigger while sending a burst of her power through her weapon to connect the chain to the ammunition, and then fired a needle with an attached chain to the edge of the rooftop.



The needle bit deep, and the chain went taut.  A second later, she was reeling in.  The pull of the chain wasn't quite enough to carry her straight to the rooftop, but the pull of the chain coupled with her ability to plant her cleats into the face of the building and run up the building face let her reach the edge of the roof.  A bit of momentum, one hand and her cleats gave her what she needed to hop over the roof's edge.



Running across the rooftop, she used her index finger to flip the switch, severing the chain, then reconnected the chain to the next piece of ammunition as her free hand loaded it into place.  It took her a second to spot the vague blur that was Shadow Stalker, almost three buildings ahead of her.  The girl was practically gliding as she fell, moving more horizontally than vertically.



It was a drop to the next rooftop, Flechette noted.  She touched the front end of the needle that was mounted in her arbalest, used her power on it.



Capes with the `breaker' classification were generally those who had some ability to `break' the natural laws of the universe as far as those laws applied to them.  Shadow Stalker was one.  Scion was apparently another.  There were others who could slow or stop time in relation to themselves, change their effective orientation in respect to gravity or make themselves effectively larger without the exponentially increasing the stresses that the increased size and mass would normally place on their body.  Almost always, such powers came with some physiological changes that let them manage despite the altered environment they were effectively operating in, allowing them to breathe and walk at the very least.



Flechette wasn't a breaker, though her power came close.  Technically, she was a striker, a cape with the ability to apply some effect by touch or at point-blank range.  The striker classification could include certain breaker effects as they were applied to things \emph{other} than the cape themselves, but not always.  Other strikers included those who used energy weapons, those who had certain kinds of superstrength that weren't accompanied by durability and those with pyrokinesis or such that didn't extend more than a foot around them.  The way she used her ability, coupled with the intuitive understanding of angles, trajectories and timing she got from her secondary powers, gave her a low rating as a `blaster'.  A cape with a ranged attack.



She infused the three-foot length of sharpened metal that was mounted in her arbalest with her power.  The more power there was in it, the less it was affected by the natural laws of the universe.  Focusing more power into an object meant gravity, air resistance and general physics held less and less sway over it.  She could tune it, make the effect longer lived, shorter lived or bias the effects to allow for more of one element or less of another.



She could do other things, but the primary benefit, the easiest thing to do, was making her ammunition punch through anything.  It would glue itself in place on impact, if she had the effect wear off at the right time, and she was very good at timing things.  She could charge the metal of her cleats so they bit into any surface, and though it was too slow to be used defensively unless her foe telegraphed their attacks, she could make her costume frictionless.



She fired the needle through the corner of the roof just in front of her, and it passed through without resistance.  It continued on to strike the rooftop below and in front of her, nestling in deep as the effect wore off, bonding on a molecular level to the material around it.  The chain stretched down at a fifty degree angle, taut.



Flechette stepped forward, onto the chain.  The space between the spikes of her cleats made for a groove the chain could run through.  She slid down, one foot behind the other, arbalest held behind her with the chain reeling out, a safety measure in the event she slipped or was pushed off, with the added advantage that it allowed her to control the speed of her descent.



When she was close to the rooftop below, she cut the chain, let herself drop down.  She was running the second her feet met the surface, using the momentum from her slide.



It was tiring, constantly running, but she didn't want to look bad in front of Shadow Stalker.  She was going to spend weeks with this team, and Shadow Stalker was the only other girl present that was close to her own age.  Doing double shifts of patrols, eating, showering, relaxing with her teammates, day in and day out, it would drain the life out of her if she had no friends to do it with, if she had no conversation and camaraderie.



At least this wasn't so different from the exercise she got on her nightly patrol back in New York.  The problem was that this city was unfamiliar ground.  The buildings didn't match together well, the skyline was jarring, didn't flow.  Back home, traveling from rooftop to rooftop wasn't much harder than running, with the use of her grappling hook to move her every minute or two.  Here, it was a jerky, stilted exercise, slow, awkward, demanding use of the grappling hook for nearly every building.



It wasn't something she did often, but after too many steep ascents followed by steep descents, she bridged a gap to a more distant building with her chain, forming a horizontal tightrope, and ran along it.



Shadow Stalker was waiting for her when she got to the other end.  She did her best not to pant for breath.



``Don't you run out of chain?''



Flechette turned, reached over her shoulder to tap her back. ``Tinker teammate back home specializes in replication and cloning.  Small pack back here consumes energy from a small fusion battery to create a steady supply.  I've also got a kit back at the base that makes me a fresh stock of bolts.''



``I could use one of those.''



``Why'd you stop?  You see something?''



``Come.''



Shadow Stalker led Flechette to the edge of the roof.  Looking down, they could see a group of men in a loose half-circle around a middle-aged woman.  The woman was backing away from the men, who were gradually closing in.



``Why haven't you done anything yet?!''  Flechette gasped.



``These things go smoother if the culprits are clearly committing a crime when you step in--''



A man grabbed the woman's wrist, and she pulled back, struggled.  She screamed, attacked the man, only to get punched and knocked back on her ass, landing in the shallow water.



``--And there we go.''  Shadow Stalker leaped from the rooftop, falling at a normal speed, slowing to an almost gentle floating descent when she was partway down.



\emph{You only need to wait like that if you're going to be violent}, Flechette thought to herself.  \emph{Why?  When she has the tranquilizer bolts?}



And Shadow Stalker had neglected to inform command.  Flechette reached for her ear, where an earbud was nestled in the canal. She squeezed it twice.  ``Console, woman under attack by twelve or so ordinaries.  Shadow Stalker and Flechette stepping in.''



``Acknowledged,'' a voice in her ear responded, ``Good luck.''



She fired a bolt into the corner of the rooftop, then jumped, rappelling down.



Shadow Stalker was already engaged by the time Flechette arrived at the fight.  In a matter of heartbeats, Shadow Stalker answered Flechette's unspoken questions.



The other heroine didn't flinch as one of the men swung a baseball bat at her – the weapon passed harmlessly through her head.  In response, she stepped back, materialized from her shadow state, raised a crossbow and shot him in the side of the neck.  A fraction of a second after the glass arrow stuck in her target's neck, Shadow Stalker stepped forward again, driving her armored elbow up at an angle at the spot where the bolt had struck home.  Glass shattered and the combination needle-arrowhead was violently dislodged.  The man went tumbled with a splash, going limp before he hit the water.  The side of his neck and the corner of his jaw were a bloody mess of cuts and embedded broken glass.



Shadow Stalker wheeled around, then simultaneously slammed the top of her right crossbow into her left forearm and her left crossbow into her right arm.  There was a barely audible click as cartridges loaded into the top of each crossbow.  She extended her arms to fire at the two of the men closest to the woman.  They dropped on their backs in the water, splashing.



Realizing what they were up against, the group began to scatter.  Flechette raised her arbalest, shot one bolt so it struck a wall just in front of one man's throat.  Still running, he ran headlong into it, clotheslined himself, and fell over, gasping and gurgling.



She spared a glance to double check he wasn't in a position to drown, which very nearly cost her.  One of the thugs turned to attack her, drawing a gun, but she had a bolt loaded and fired off before he could aim it, spearing through the gun's barrel and out the back, to strike a wall.  She loaded another bolt even as she was already pulling the trigger to fire it, so it was sent out an eye-blink after it was in place.  The shaft of metal struck the thug through the crotch of his sagging jeans, pinning them to the wall he was backing up to.  He didn't scream, so he clearly wasn't well endowed enough to get hit anywhere important.  Flechette wasn't exactly an expert -or even a novice- in that sort of thing, but she was ninety-nine percent sure that men didn't dangle nearly to their knees.



Made lightweight by her power, Shadow Stalker leaped to the nearest wall, then vaulted herself off, careening directly toward three of the retreating men.  As she landed atop the one in the front, she dropped out of her shadow form, returning to her normal weight.  Planting her feet on his shoulder blades, she combined the force of her weight and her momentum with a downward kick of both feet, driving him into the water, hard.  She went shadowy a half second later, becoming almost invisible in the gloom of the empty lot, effortlessly reorienting her now lightweight body to land on her feet.



Both of the men behind Shadow Stalker attacked her, one swiping a knife at her, the other kicking for the small of her back.  Smoky, dark flickers appeared where limbs and weapons passed through her.



Almost casually, she holstered her crossbows, then straightened up.  A flurry of other attacks passed through her.



One man hesitated, seeing the futility of what they were doing, and Shadow Stalker took the opportunity to drop the shadow state.  She leaned out of the way of one desperate punch from the other man, then grabbed him.  She seized him by the shirt-front, pulled him forward with a hard tug on his collar and a counterclockwise turn of her body, then brought her right knee into his ribs.  He fell with a splash.



\emph{Metal kneepad}, Flechette noted.  \emph{That's going to hurt}.



The other man attacked, but Shadow Stalker went shadowy just long enough for his knife to pass through her, then slammed her metal mask into his face.



While he swayed back, stunned, blood streaming from his nose, she reached out and grabbed him by the lower jaw, her fingers digging into the bottom of his mouth.  Instinctively, desperately, he bit down, hard, but the construction of the girl's gauntlets was good enough to safeguard her fingers.  She used her grip to pull him to one side as she'd just done with his compatriot, helped by a swift kick to the side of one leg.  Rather than use her knee to deliver the telling blow, she brought the heel of her free hand against the gap between the man's skull and his jaw.  He screamed, crumpled toward the ground, his hands moving to where the strike had hit.



Shadow Stalker waited a moment before letting go, forcing him to twist and squeal in agony before she let him finish collapsing.



After watching him a moment, perhaps to be sure he wouldn't retaliate, Shadow Stalker glanced at Flechette.  ``Your man there is getting loose.''



Flechette had been caught up in the spectacle of watching Shadow Stalker fight.  A kind of horrified fascination.  She saw the thug she'd shot in the crotch, on his back in the water, his pants still fixed to the wall.  He was struggling to work his legs out of the jeans.  She loaded a shot and fired a bolt just beneath his armpit, nailing his sweatshirt to the ground.  Another just above his opposite shoulder and behind his neck secured him.



Shadow Stalker was chasing one of the stragglers.  Going shadow-light, she closed the distance in two long paces, leaving ripples and small disturbances in the foot-deep water, rather than splashes.  As she reached the man's side, she dropped the shadow state, gripped his ear and used one leg to trip him.  With the grip his ear afforded her, she thrust him face first into the ground with enough force that he couldn't absorb the impact with his arms.  Water sprayed around them in the wake of the hit.



Flechette reached into her belt and withdrew a handful of darts, each nine inches long.  She channeled her power into each, and then flung them at the feet of the two remaining thugs, catching the edges of their shoes.  Their shoes fixed firmly to the ground and they fell awkwardly.  Two tranquilizer bolts appeared in the rear end of one and the upper thigh of the other.  Shadow Stalker.



Which finished the fight.  None of the men were left in any state to run.



Flechette palmed one of her throwing darts, glanced at it.  She'd been with the Wards a year before she had been given the arbalest and the chain reel.  Her darts had been her weapon of choice for a long time, alongside a rapier she'd eventually retired after too many fights using it had turned out badly.  She hadn't had the heart to change her codename, even if it didn't quite apply anymore.  Maybe when she graduated to the Protectorate.



``Hey,'' Shadow Stalker called out, disturbing her from her thoughts.  ``Here!''



\emph{Tired,} she thought, \emph{mind's wandering.}



Flechette caught the device Shadow Stalker threw to her.  Investigation revealed it to be a small, thin, round device with a single button on top.  ``Haven't seen one of these since training.''



``Times like this call for 'em.  City wants us on patrol, not sitting around with our thumbs up our asses, waiting for the cops to cart these fuckers off,'' Shadow Stalker kicked one man in the side, so he flopped over onto his back, no longer face down in the water.  He grunted.



Flechette winced.  \emph{That girl is a little too comfortable with violence for my tastes.}



While Shadow Stalker ensured that the man with the cuts on his neck wasn't bleeding out, Flechette  loaded another bolt into her arbalest and fired it into a spot on the wall, two floors up.



She walked briskly to the two men that had just been darted.  She bent down and used her left hand to wind the coil of the restraint device around his left foot, then did the same for the next man's right foot.



She tossed the restraint device over the bolt she'd embedded in the wall, a metal thread trailing behind it.  She caught it as it fell, then connected it back to the cord, forming a loose loop that encircled the bolt in the wall.  She pressed the button, and the cord retracted, pulled tight around the pole, then continued retracting.  The two thugs were pulled off the ground, so that each hung from the wall by one ankle.



The device would signal nearby police and PRT officers and direct them here.  They'd use their own equipment to make the restraint device lower the men so the thugs could be brought into custody.  The cord was difficult to cut with conventional knives and saws, and those caught wouldn't want to cut it either, given how they faced a long drop face first onto pavement.  Any buddies of theirs would have a hell of a time getting to them and cutting them free, as well.



She walked over to the man she'd clotheslined, who still hadn't finished gasping, nor had he collected himself enough to run.  She grabbed his wrist and forced it behind his back.



As she hauled him to his feet, a collision made her stagger back.  It hadn't been directed at her.  No, it was the man she held that slumped, almost insensate.  He hung his head, a trail of blood dribbling from his lip.



Seeing a movement just outside her blind spot, opposite the man, Flechette pushed her captive down and away.  She had to evade the weapon as it swung towards her head.



It was the middle-aged woman that the men had been attacking.  She held a metal trash can lid in two hands.  Oblivious to Flechette, she swung the lid down at the man's head.



``Hey!'' Flechette shouted, ``Stop!''



She reached out to grab for the lid, but a hand on her wrist stopped her.



``Let her,'' Shadow Stalker spoke.



The woman kicked the man in the ribs, hard, then struck him with the flat of the metal lid.



``You fuckers!'' the woman screamed.



Stunned, Flechette spoke to Shadow Stalker, ``The hell?  He's not in a position to defend himself!''



``Doesn't deserve to.''



``She's going to kill him!''



``Better that we give her another few swings than render her powerless for the second time tonight,'' Shadow Stalker spoke.  ``Or she won't get over it for a long time.  We'll stop her before she goes too far.''



``No, this isn't right.'' Flechette pulled her arm free of Shadow Stalker's grasp, then grabbed the woman's wrist, stopping her as the lid was brought back behind her head.  Not entirely to the woman, she spoke, ``You're better than this.  You have to be.''



The woman resisted, tried to pull free to make another swing.  When Flechette maintained her grip, the woman used her free hand to throw the lid down on top of the man.



``Stop,'' Flechette spoke.  As the woman struggled, she turned to bark a command to Shadow Stalker, ``Help!''



``I'm on her side, to be honest,'' Shadow Stalker didn't move.



``So am I,'' Flechette grunted as the woman shifted her weight towards her, knocking her off balance.  ``Which means stopping her from doing anything she'll regret!''



``Let me go!'' the woman shouted at her, ``Fuckers like this hurt my daughter!''



``Is she here?  Your daughter?''  Flechette asked.



``She's home, it- it happened last week!  Let me at him!  Fuckers!''



``Stop attacking him and I will!''



The woman didn't have a response, beyond continued struggles.  Though Flechette kept to an exercise regimen, spent four nights a week in the gym, she was still only seventeen, and the woman had a good fifty or more pounds of weight advantage.  The woman pulled free and staggered back, gave her an angry look.



When the lady stepped forward, toward the fallen, bloodied man, Flechette stepped in her way.  The woman didn't back off, so Flechette raised her arbalest a fraction.



That was apparently enough.  The woman scowled further, then turned and fled the scene, half-running, half-limping.



``Thanks for the backup,'' Flechette spat the words to Shadow Stalker.



``Told you, I don't do the backup thing,'' Shadow Stalker bent over the unconscious man, turning his head to investigate his injuries.  ``He'll live.  Him and his buddies deserve what they got.''



``That's not your call to make.''



``Sure it is,'' Shadow Stalker retrieved another restraint device and quickly strung the man up beneath a metal frame meant for an air conditioning unit.  ``Times like this, we're cop, judge, jury and if it \emph{really }comes down to it, executioner.  We're the ones with the power.''



``No.  That's wrong.''



``Suppose we'll have to agree to disagree,'' Shadow Stalker turned her back, preparing another restraint device.



Flechette huffed, angry.  She didn't want to get into a shouting match, wasn't sure what to say to convince the girl.  ``You can finish your patrol alone.''



``Whatever,'' Shadow Stalker replied without looking back, ``If you want to be like that.  I'm only on the team because I have to be, so you're doing me a favor.  Prefer to fly solo.''



\emph{Three strikes,} Flechette thought, as she strode away.  Nearly being shot for saying hello, the way Shadow Stalker had delayed helping the woman, and now this.



She'd give the other girl the benefit of a doubt.  Maybe Shadow Stalker had some unresolved issues, maybe it had been a rough week.  But for now, she needed to calm down and wait long enough to think more objectively about what had happened.  Then she'd decide whether to deal or to tell her new team leader.



\emph{Fuck}.  She felt profoundly disappointed.  She \emph{wanted} to like the other heroine, but this was too much.



She had one other thing she had wanted to do tonight, before she finished her patrol, went back, showered, ate and unpacked.



She squeezed the bud in her ear twice, ``Console?''



A brief pause, then a voice in her ear, ``Kid Win on the console.  Hi, Flechette.  Deal with those guys okay?''



``Guys are dealt with but\ldots I'm going to do the rest of my night's patrol alone.''



``Sorry.  I should've warned you.  Tends to be easier to work around her.''



\emph{So she's always like that}.



``This is unfamiliar territory for me. I might need you to brief me if I run into a cape, so I know what I'm potentially running into.''



``Of course, I'm not going anywhere.''



``And on that subject, I remember meeting someone when I was in town for the attack.  What can you tell me about the cape with the stuffed animals?  Pariah, par--''



``Parian,'' Kid Win replied.  ``A parian doll was a kind of doll about a hundred and fifty years ago.  Though Parian's costume is actually closer to a more classical Victorian style porcelain doll, from the same era.''



``Oh.''  \emph{That was random.  What kind of guy knew that much about dolls?}



He went on, ``She's a rogue.  Fashion student with the costume and stuffed animals as a gimmick to help her build for a professional reputation and stand out.  Tentative rating of Master-6, but we haven't really seen her fight, outside of the Leviathan encounter.''



``Student.  So she'll be near a college?''



``College is gone.  Kaput.  Um, let me see.  Last we heard, she was situated between the spot where the college was and the lake downtown.  If I remember right, there's going to be a fairly thin strip of places there that are intact enough to live in.  Vista ran into her the other night, but she's asleep right now and we're behind on paperwork so\ldots''



``So you don't know exactly what happened, and I'd be going in blind.  She's harmless though?  This Parian?''



``Nobody's harmless at a time like this, Flechette,'' Kid Win replied.



``Right.''  Flechette thought of the middle-aged woman beating her attacker bloody.



``Listen, easiest way to get to that area, you'll find the lake to the northwest, walk the perimeter of it to reach the north end.  The area she could be staying at should only be a block or two wide.  If she's even awake.  I've got Clockblocker buzzing in, probably to check in for the night and give me the cliff notes on his nightly patrol, so I'm going silent until you need me, k?''



``Sure.''



Flechette gauged the direction of the ocean, deemed that east, and then headed northwest as Kid Win had suggested.  She traveled at ground level, wading through the water, to make faster progress.  Nothing to prove, now that she had stopped patrolling with Shadow Stalker.



It didn't take long to find the `lake' Leviathan had made in the downtown area.  Given that the streets were flooded with water anyways, the crater itself was distinguishable only by the barrier around it, and a dark shadow beneath the water where there was nothing beneath to reflect light.  Hulks of fallen buildings sat in the center of the water.  The orange light of a fire on the top floor of one of the buildings suggested that someone had swum to one of the buildings and was staying there.  Maybe one of the safer places to be.



The crater was surrounded by orange striped barriers with flashing lights and portable chain link fences that were chained together.   The fencing formed a solid barrier around the hole.  She walked with the fence to her left, which roughly halved the area she had to keep an eye on, in case of approaching trouble.  Her right index finger was just below the trigger of her arbalest, and her left hand clutched a handful of darts.



The massive sinkhole Leviathan had made was roughly circular, but it was large enough that she couldn't say for sure when she had turned and started moving more west than north.



Fresh graffiti stained buildings, some warning people to stay away, others were the crude pictographs of hobo signs.  One neighborhood had used the debris of fallen buildings to form makeshift barricades in alleys and in front of doorways.  There wasn't much intact housing here – the sinkhole sat to her left, and two blocks to her right, from what she could make out in the moonlight, the buildings were too damaged to serve as living accommodations.



At one intersection there were two parallel, vertical lines spray painted in yellow on opposite walls.  Traffic cones, some broken, an orange striped barrier and the remains of one yellow raincoat sat in the water, much of it weighed down by rubble.  Together, the organized debris formed a brightly colored line joining the marks that had been spray painted on the wall.



She stepped over the line, and immediately felt a resistance.  It took her a second to figure out what it was – a thread caught the moonlight.



There was a muffled splashing sound, and a twelve-foot tall gorilla leaped from the nearest rooftop to land directly in front of her.  It swung its arms wildly in front of it, missing her, then slammed both knuckles down in the water, crushing one side of the orange striped barrier.  Flechette raised her arbalest to shoot, then stopped.



It wasn't real.  Damp cloth, stitched together.  And it was blind.  It wasn't acting as though it could see her.



She dropped the arbalest, backed over the line, and then waited.



Parian arrived at a run, feet splashing in the water.  She spotted Flechette, and the gorilla moved to place itself between the two of them.



\emph{Her creations can only see what she sees}.  \emph{They're puppets}.



``Stay back,'' Parian warned.  She peeked out from behind the gorilla.  Her mask, a doll's face, was smudged, and a crack ran from the corner of one eye to the ear.  She wore a frock, different than the one she had worn for the Leviathan fight, but it was wet, dirty, and some of the lace had torn.  There was a wood chip in the damp golden curls that were otherwise too perfectly coiled to be real hair



``I'm staying back,'' Flechette assured the girl.  ``Remember me?''



``Yes.  You talked to me before the fight, pulled me away from that horrible little girl.''



``Yeah,'' Flechette smiled, shrugging.  She stepped forward.



``Back!''  Parian called out.  The Gorilla slammed its knuckles against the ground again, then lurched forward, one fist raising as if to deliver a massive punch.



Flechette obeyed, backing up another two steps, hands raised.  The gorilla's fist stayed where it was.



``I'm a hero.  Member of the Wards.  I'm in town for a little while.''



``Doesn't matter.  I made a deal.  Me, my friends and my family get a place to stay here, a fair share of the food and water.  In exchange, I keep people from entering.''



``I'm a \emph{hero},'' Flechette stressed the word.  ``I'm not going to cause trouble.''



``I don't know you're telling the truth.  Nothing saying you couldn't be lying.''



``I have ID.''



Parian shook her head.  ``It doesn't matter anyways.''



The frocked rogue climbed up to stand on top of the gorilla's shoulders.  She added, ``I made a deal.  I'm keeping to it.  One hundred percent neutrality.  You trespass, I fight you.''



\emph{And I'd almost definitely win,} Flechette thought. \emph{You may even know that, but you'd fight me anyways}.



``Okay,'' Flechette replied, trying to sound reassuring, ``I won't step over the line.  I heard you were around here, you're one of the only recognizable faces for me here, I thought I'd stop by, see how you were doing.''



``Coping,'' Parian answered.



``Good, good,'' Flechette sheathed her arbalest, hoping the rogue would feel safer.  ``Look, I'm here if you need anything.  If people make trouble and you're not strong enough to protect that neighborhood there, or if you need resources that you couldn't get otherwise, like names or medical services, call me.  Can I give you my card?''



The gorilla lowered his raised fist, reached forward with palm upturned, and Flechette fished in her belt for her cards.  Slightly damp, but readable.  She placed it in the center of a sopping wet hand crafted out of black denim.  The gorilla's palm was surprisingly firm.  Hard.  Its shape was a little too humanlike, in comparison to a real gorilla, maybe.  Not that it mattered.



``Okay,'' Parian spoke, as the gorilla handed her the card.  Her voice was a little softer.  ``Phone lines are down, but cell phones work around here.''



``You guys need anything here?  I don't know what the situation is with supplies, just got into the city a few hours ago.  Don't know how that stuff is being distributed, but I could see about making sure you guys have something.''



Parian sat down cross-legged on the gorilla's shoulders.  ``Yeah.  We're low on fresh water.  This stuff we're wading in has too much salt content, and you couldn't even boil it clean if you wanted to, I don't think.''



``Okay.  Fresh water.''



The doll girl shifted her weight to put the card in the front pocket of her lacy apron, fumbled with it.  Flechette spotted a tremor as the girl put the card away and moved to clasp her hands in her lap.



\emph{She's shaking}.



``Hey?'' Flechette asked.



``What?''



``Seriously, are you okay?  You holding up?''



Parian turned, looked behind her, as if checking anyone was listening.



``I hate fighting.  Hate confrontation.  Even this, being here, having just thought I might have to fight you, fight \emph{anyone}, it makes me feel edgy.  My teeth are chattering and I'm not even cold.''



``You faced down Leviathan.  You did better than a lot of people.''



``Do you know how long it took me to get my head together?  To actually step up and help?''



``But you did.  You stepped up.  Give yourself credit.  You're strong.''



``I want this to be over.  I'm so, so scared that someone's going to come and try to loot this place and I won't be able to do anything.''



``You've got my card.  I can't promise I'll arrive immediately, but I'll be staying at the Wards headquarters, which isn't too far.''



Parian nodded.  Quietly, she spoke, ``That helps a lot.  More than you know.''



``And I can come by on my patrols, if you want.  Check everything is okay, give you an update on what I can do about supplies.''



Parian hesitated, ``Please do.  If you pluck the strings twice, I'll know it's you.  I'm using my telekinesis on the strings, I'll feel it.''



``Deal.  I'm Flechette, by the way, in case you didn't know.''



``Oh.  Um.  I didn't.  My name's Sab--'' Parian stopped, made a barely audible groan.



``It's okay,'' Flechette suppressed the urge to smile.  Sabrina?  Maybe.  Sable?  No, the b pronunciation was different.



``I'm an idiot,''  Parian spoke.



Flechette paused, then removed her visor.  ``Lily.''



\emph{I need people I can trust}, she tried to convince herself, even as she knew she had other reasons.  Stuff like this could get her in serious trouble with the Wards.



Parian hesitated, then reached up and removed her mask.  Though her clothing style was western, her wig all blonde curls, her face was dark, middle eastern.  There were bands of metal extending from the edges of her face to the middle of her cheekbones, her chin and her forehead.  Mounts to keep her mask in position?  She had full lips and large, dark eyes. ``Sabah.''



\emph{Cute}, the thought struck Flechette.  \emph{Funny to think she's older than me.}



``Nice to meet you, Sabah.''



``I'm still not letting you over the line,'' Sabah warned.  She looked so small, up on the gorilla's broad shoulders, the threat held little gravity.  Maybe, Flechette considered, it was intended more for Sabah than for her.



``Okay,'' Flechette donned her visor once more, ``But maybe you want to walk with me?  Do a patrol of the perimeter of your territory?  I'll stay on this side.''



Sabah put her mask back on, and for a second, Flechette thought she would say no.



``Okay.  Thank you.''  Parian dropped her legs down to either side of the gorilla's neck as it moved forward. To stay decent, the girl pressed her hands down on the lap of her dress, leaning forward a little.  It was a little thing, that bashful modesty, but Flechette felt as much of a rush watching that as she did running across her chain/tightrope with a five-story drop below her.



She didn't let it show.  Instead, she smiled and started walking, hands clasped behind her back, darts clasped in one hand in case of trouble or ambush.  The gorilla crossed the yellow line and sort of half-ran, half-loped to catch up, move beside her.  It slowed to a plodding, gentle walk



Flechette was secretly relieved.  She knew she'd manage for the duration of her stay, now.  She'd made a connection, even if it wasn't with someone on her team.  She wasn't in this alone.



``So, you're a fashion student?'' she asked.





