





``Welcome to Parahumans 103: Theories and Patterns.  I see we have a packed auditorium, and according to the enrollment list, we have no less than three hundred students taking the TV course.  A bump up from the last two trimesters, so I must be doing something right.''



Clockblocker looked around the room.  Six PRT uniforms sat in the front row, helmets off, three with notebooks open on the desks in front of them.  Weld and Flechette sat in the desks closest to the door, exchanging murmured words as the professor on the screen began going over the course syllabus.



Glory Girl sat just in front of him, wearing a black, long-sleeved shirt, arms folded on her desk, chin resting on the back of one hand.  Vista, odd as it was, sat beside the other heroine, had been the only one to offer any conversation.  When Glory Girl hadn't seemed interested in talking, Vista had instead offered her silent company.  Clockblocker wasn't exactly sure how Glory Girl had gotten into the Wards headquarters to attend the screening, but she was here, uncharacteristically quiet, much in the same way that Vista had been this past week.



Kid Win sat to Clockblocker's right, fidgeting by taking apart his pen and putting it back together, his eyes not leaving the screen.  Shadow Stalker was sitting as far away from everyone else as she could manage, at the back corner of the room.  She sat sideways in her seat, back to the wall, her feet resting on the seat next to her.  Her attention was directed entirely at the keys and screen of her cell phone, rather than the projector screen at the front of the room.



Only thirteen people present, altogether.



``\ldotsfor disability and pregnancy accommodations, the course syllabus gives you all the details you need on who to contact.  If you aren't already, you're going to be sick of hearing all that by the time you graduate.  We're required to go over it in the first class of every class we teach.



``So.  Let me start off by addressing and banishing some assumptions you may have.  This is not an easy class, and anyone who took Parahumans: History and Society or Parahumans: Case Studies and Powers will be aware of this.  Even for those of you who emerged triumphant from the previous two semesters should know that PARA-103 may be something of a shock to you if this is your first year of University.  Here, primarily, I will be looking for creativity, problem solving and research abilities.  Skills and abilities that, frankly, aren't stressed enough in high school.



``For this class, I want you to \emph{think}.  Parahumans.  People with powers.  They've been around for nearly thirty years.  Where did they come from?  \emph{Why} are they here?  It's common knowledge that parahumans are ordinary individuals who gained abilities.  It is too easy, however, to assume that this is the sum total of our knowledge.  I want you to think further on the subject.  For example, why does virtually every parahuman ability have some application in confrontation and combat?  Is this the nature of humans, to turn any progress to violent ends, be it science or superpower?  Or is it by design, an individual's hand at work?



``With the destructive potential of these abilities, why do so very few individuals perish in the chaotic and unpredictable emergence of their talents?  For the first two or three weeks of the class, we'll be talking about these most pivotal moments in a given parahuman's existence, these trigger events, when an individual first gains their powers, typically through some form of trauma.



``Throughout the course, we're going to be looking at correlations and patterns, both in relation to trigger events and other things.  For example, how does the nature of the trigger event shape the power?  A study by Garth and Rogers suggests that psychological stress leads to a higher prevalence of mentally driven powers.  Tinkers, thinkers, masters, shakers.  The more physical violence that is involved, the higher the bias towards physically driven powers.  Garth and Rogers suggest a sliding scale, but it may not be that cut and dry.



``A followup study by Garth touches on what we know about cape `families'.  If one individual in a family has powers, it is far more likely that others will as well.  Almost always, this trend is either descending or lateral, it seems to transition from parent to child, or one sibling to another, but not from child to parent.  We'll talk about the theories on \emph{why}.  For those of you wanting to read ahead, take a look at Garth's notes on the Dallon and Pelham families in chapter nine.  We can surmise that the different scenarios leading to trigger events may be directly related to the differences in powers, even among closely related members of a cape family.  Similar trigger events and related individuals, similar powers.  The more distant the relation and the more varied the trigger events, the more drastically different the powers they possess in the end.''



Clockblocker glanced at Glory Girl, to see if the mention of her family had stirred her interest.  She hadn't budged an inch.  Was she asleep?



He couldn't help but sympathize. \emph{ This is a monumental waste of time.  I could be out there, helping people.  Or spending time with my family}.  The Protectorate was coordinating shifts so the Wards could collectively get at least \emph{some} education in the meantime, on Piggot's orders.  Except this wasn't useful, this wasn't applicable to the ongoing crisis right here, right now, in this city.  Cooped up in a PRT conference room, learning stuff that didn't apply to actual field work.



Hell, it was on videotape, a recording of last year's lectures.  Why couldn't they watch it in their off hours?  It was just a fucked up set of priorities enforced on them from the people in charge.



He shifted restlessly, annoyed, angry.



``Trigger events are a crucial element for study, because the timing, nature and spread of these emerging powers may provide a clue as to where these parahuman abilities come from.  More women than men have powers, for example, and there are more powers in undeveloped countries than there are in industrialized ones – Some of you may remember me mentioning this fact in the 101 class, when I was talking about the witch burnings in The People's Republic of Uganda.



``Another pattern we will be exploring is the apparent effect of multiple trigger events occurring in the same time and place.  There is a very strong correlation between coinciding trigger events and individuals displaying three or more powers rather than one or two predominant ones.''



``Hey, Flechette,'' Kid Win called across the room, ``You've got a bunch of powers, right?''



She turned in her seat, ``Sure.''



``Anyone else get powers at the same time you did?''



``Not that I know of.''



``Could someone nearby have gotten their powers, without you knowing?  Way things played out?  Did any capes show up around the same time as you?''



Flechette frowned, ``Yeah.  A rather persistent villain.''



``Worth thinking about.''



Weld turned around, ``Critical thinking and applying this stuff is good, but let's not forget the lecture.  Or the other people in the classroom.''



\emph{Is he trying to get people to dislike him}?  Clockblocker wondered.



The professor on the screen was answering a student's question, ``\ldotsI think Eidolon expresses a single power.  But thank you.  Good question, and good lead-in to the next section of the course we'll be discussing.  After we wrap up on trigger events, we're going to be moving on to what we call `outliers'.  Parahumans or parahuman-related elements that deviate from the norm.  Any guesses?''



``Scion.'' A student on the TV spoke.  The camera shifted to him late, and by the time he'd responded, the professor was pointing to another.



``Endbringers.''



``Nilbog.''



``I wouldn't suggest Nilbog, but we can debate the point later,'' the professor spoke, ``Perhaps a subject for a course paper.  Scion, yes.  Endbringers?  Yes.  We have no reason or evidence to suspect they gained powers by normal means.  Another group you may or may not be familiar with are what the PRT terms Case Fifty-Threes.  Often the `monstrous' parahumans, we'll get into more depth on the subject.''



Clockblocker glanced at Weld.  The boy was digging through his canvas backpack for something.  Was he one of them?



``Weeks five and six, assuming we're on schedule, we'll pull all earlier material together and discuss the beginnings of the parahuman phenomenon.  Not for the individual, as with trigger events, but as a whole.  Where do capes come from?  There is the patient zero theory, typically working under the assumption that Scion is the source of these abilities.  This, however, raises questions about where \emph{Scion} came from.  The theory is corroborated by the case of Andrew Hawke, who came into contact with Scion on the very first sighting of the hero, only to manifest powers of his own\ldots but there are others who manifested powers without ever coming into contact with Scion or entering a location where Scion had visited.''



``There's the viral theory, supposing some advanced virus, though it is flimsy at best in justifications, with no identified culprits, method of transmission or explanation as to how it provides the actual powers.  The genetics theory is popular, but has been thoroughly debunked.  We're going to talk about \emph{how} it was debunked\ldots''



Clockblocker felt a vibration at his wrist.  He reached inside his glove to get his cell phone.  A text.



From: Mom



Dad's not doing well.  You may want to come by the hospital.



He stood, and Weld turned to give him a look.  He ignored the metal skinned boy, headed for the back door of the classroom, his keypad beeping as he dialed the number.  It was ringing as he closed the door behind him.



``Mom?''



``Dennis.''



``How bad is it?''



``As bad as last weekend.  Worse.''



He closed his eyes.  More statement than question, he said, ``He's not getting better.''



``No.''



``Okay.  Do you need me there?  I can use my power, buy the doctors time to think or get prepared if there's a crisis.''



Her voice was tight.  ``No, Dennis.  It's not that kind of situation.  They've got him on a respirator, and the doctors don't have much hope he's going to be able to breathe without it, again.  The antibiotics can't fight the infection on their own.''



``So he's going to die.''



``I'm sorry.''



``A few hours?  Days?  A week?''



``The doctor says it'll be the next few days.''



He clenched his fist, relaxed it.  \emph{Not fair.}



``Hey, mom?  Listen, I've got to run.''



``Come by, Dennis.  Before it's too late.''



``I'll try.''



``I love you.''



``Love you too.''



He hung up, paused to compose himself.



\emph{Not fair.}



Stepping back inside the classroom, he returned to his seat, but didn't sit down.  Instead, he stepped up a little further to where Glory Girl sat and touched her shoulder.  When she raised her head, he pointed to the door.  She nodded, stood.



When they were both in the hallway, he spoke, ``Sorry to pull you away from that.''



She shook her head, golden curls swinging, ``Not missing anything.  I've already taken this class.''



``Oh.  Then why are you here?''



``New Wave may be disbanding.  My mom suggested that if I wanted to keep being a hero, I should consider joining the Wards.  So I'm here, checking things out.  Your leader and director okayed it.''



``Are you?  Joining?''



``Don't know.  They're willing, if I agree to some extra rules and stipulations.  They'd be putting me on probationary membership, like they did with Shadow Stalker.  I came by to get a sense of things, see if it'd be worth going through the hassle instead of going solo.  I thought maybe I was ok with doing it until I saw the portraits in the lobby.  Now I'm not so sure.''



Clockblocker nodded.  She didn't need to explain.  Where the Wards' portraits hung in the lobby of the PRT offices, the portraits of Aegis and Gallant had been reprinted in black and white, surrounded with thick black frames.  They had been repositioned to be just above the front desk and below the PRT logo, with wreaths and flowers beneath, tokens from the PRT employees.  The building wasn't open to the public, and was surrounded by PRT squads, but the public would get their chance to pay respects.



Glory Girl had lost three people she was close to on that day.  Gallant – Dean when out of costume – was a loss she shared with Clockblocker.  Her boyfriend, his friend.



``I know it's crass, I know you guys have rules,'' he spoke, ``I'll understand if you get angry.  But\ldots my dad has leukemia.  He was a few days into some pretty rigorous treatments when Leviathan came.  He got hurt when one of the waves hit, and some infection got at him through the wounds.  He has pretty much no immune system, doesn't have the strength to fight it off.''



``You want me to ask my sister to use her power on him.''



``Please.''



``Okay.''



The response startled him.  He looked up at her, caught off guard.



She explained, ``I'm not promising anything.  Like you said, Amy has her rules about taking requests.  But I'll see if I can convince her.  Again, no promises.''



``Thank you,'' he said, ``Really.''



``And if you want to pay me back, maybe tell me about Gallant sometime.  Share some stories I wouldn't get to hear otherwise.''



``For sure.''



The door opened, and Weld stepped out into the hall, followed closely by Vista.  Clockblocker felt a pang of annoyance, bit his tongue before he could say anything.



``Everything okay?'' Weld asked.



\emph{I could tell them, }Clockblocker glanced at Vista\emph{, but the rest of the team would find out.}\emph{They don't need another thing to worry about.}



``Things are okay,'' Clockblocker spoke, carefully.



``We paused the video, waiting until you guys are ready.''



``Alright,'' Clockblocker replied.  He added, ``Thank you.''



``I'll trust you have reason for this,'' Weld smiled slightly, showing a row of white metal teeth, ``But don't take too long.  You're on patrol at two this afternoon, and that doesn't allow us much leeway for delays if we want to finish watching.''



``Alright,'' Clockblocker repeated, his tone growing impatient.  He watched as Weld returned to the classroom, shutting the door behind him.  To the closed door, he muttered, ``Tool.''



``He's trying,'' Vista piped up.  ``It's hard to be leader, but he's working hard.''



``That's my whole problem with him,'' Clockblocker answered, annoyed, ``He gets on our case about patrols and training and paperwork, then turns around and says he's not asking us to do anything he isn't doing himself.  Except he only sleeps one or two hours a night, he barely eats, doesn't need to use the washroom or shower.  He's got no friends or family here to look after.  He can \emph{afford} to work hard.  He's a f\ldotsrigging robot.''  He censored himself for his junior teammate.



Vista shook her head.  ``That \emph{robot, }and he's not really a robot, by the way, is doing as much paperwork as the rest of us put together.  He only makes us do the paperwork he \emph{can't} do himself.  Even if he doesn't have to.  That gets brownie points from me.''



His temper flared.  ``What, are you channeling Gallant, here?  Standing up for\ldots'' he trailed off before he could finish.  Realized who he was talking to.  ``Shit, no, I\ldots''



Vista just stared at him.  After a second, her eyes got shiny, and she looked down at the ground, an angry expression on her face.   She wheeled around and ran down the hallway.



He moved to chase her, stop her, but the hallway folded together, letting her reach the end in two strides, snapping back to its full length as she passed along it.  She rounded a corner in the distance.



He looked at Glory Girl, his voice small, ``I'm sorry.''



She answered him with only a glare.  He wondered if she would hit him.



She relented, looking in the direction Vista had run off.  ``It's okay.  We're all worn down, at the end of our ropes, and you're worrying about your dad on top of that.  You get one pass from me.  One.''



He nodded.



``But you'd better go after that girl and apologize.  Because the way I heard it from Kid Win, \emph{you} were the one who told everyone else to be extra nice to her, because she was taking it hard.  \emph{You} convinced Shadow Stalker to play nice, and from what Kid Win said before class started, that was a pretty big deal.  Maybe I'm wrong, I don't know your team like you do, but I'd guess that if you don't fix this, your team won't forgive you for a long time.''



``Yeah,'' he swallowed.  Was she using her power?  He was getting a bad vibe from her.  Like he was locked in a cage at the zoo with a murderous jungle cat.



She poked him in the chest with a finger.  ``A \emph{real} apology.  You own up to what you said and did, acknowledge that it wasn't fair of you to say, and you promise to do better in the future.  That probably means you should cut Weld some slack, because Vista wants you to.''



``Okay.  Right, okay.''



She pushed his shoulder, making him stumble in the direction Vista had gone.  \emph{Easy to forget how strong she is}.  ``Now go.''



He ran.



\emph{Definitely don't get the sense I'm forgiven}, \emph{there}.



He checked two empty rooms and made one nervous check of the women's bathroom before he found Vista halfway down the stairwell at the rear of the building.  She had one leg up on a higher stair than the other, her hands clasped around her knee.  She turned her head partway, acknowledging that someone was there, then wiped at her eyes with the sleeve of her costume.



``I'm sorry,'' he spoke to her back.



``You're a jerk.''



``I am.  I'm the worst jerk.''



Vista twisted around to look up at him, ``You said that in front of Glory Girl, too.  He was her \emph{boyfriend}.''



``I know.  She said she understood and that it was okay, but I don't know how true that is.  Before I figure that out and work out how to make it up to her, I want to make sure \emph{you're} okay.''



She hung her head.



It was a long time before she spoke.  ``He was the reason I looked forward to coming here every day.''



He walked down the stairs and sat down next to her.  ``Yeah.''



``I knew I didn't have a chance with him.  He was way older, he was rich, handsome.  He was dating Glory Girl, or they were just getting over a breakup, or he was starting to patch things up with her for the millionth time.  There was never a good time to talk to him one on one, unless we were out on patrol together, and I dunno what I would have said if there had been a chance.''



``He liked you.  He was fond of you.''



Vista gave him a sidelong glare, ``Are you lying to me?''



``No!  No.  I'm saying he actually enjoyed doing patrols with you.  Never had an unkind word to say about you-''



She interrupted, ``He didn't have an unkind word to say about anybody.''



``Not exactly true.  When Piggy caught on to the fact that Shadow Stalker was doing solo patrols every night, made us take turns going with her, he had a few things to say.  About both Piggy and Shadow Stalker.''



Vista smiled slightly.



``He enjoyed your company, Missy.  There were little signs, but I believe it.  When Triumph or Aegis assigned him a patrol shift with Kid Win, Browbeat or just about anyone else, it was `okay', or `yes sir'.  But when it was with me or you, it was `great' or he'd just smile really wide, like it had made his night.  It sounds dumb when I say it out loud-''



``No. I kind of noticed that too.  I thought it was wishful thinking.''



Clockblocker sighed, ``He was a good guy, and it's shhsss\ldotsucky-''



``You can swear around me, Dennis.  I'm thirteen, not eight.''



He smiled a little behind his mask, feeling embarrassed.  ``Okay.  Sorry.''



More seriously, he admitted, ``It's shitty of me to snap at you for doing what he would do.  Glory Girl said I should let the grudge toward Weld go, partially for you, and she's right.  \emph{You're} right.  I was, \emph{am}, angry.  At the pointlessness of what happened, what's still happening out there.  I get frustrated and angry when I'm here, because I feel like I should be out on the streets.  I get pissed off when I'm out on patrol because I feel like I should be with my family\ldots but when I'm with my family, I feel frustrated and helpless because I can't do anything there\ldots''



He stopped himself before he admitted the full extent of his difficulties back home.



``\ldotsI was taking it out on the new guy, when he probably doesn't deserve it.''



Vista let her head rest on his arm.



``I miss the old Dennis.  The guy who picked a sorta rude codename and announced himself in front of the news so Piggy and the other people in charge couldn't really make him change it.  Because it was funny.  Because he liked pushing the limits and because he saw this all as something fun.  The new Dennis is so angry.  Now I guess I get why.''



``Aren't you?  Angry?  At everything that's going on?  At the unfairness of what happened?''



She shook her head, which amounted to rubbing her head against his shoulder.  ``Yeah.  But you can't let it consume you.  If you really don't like Weld, you don't have to force yourself to get along with him.  But don't stay like this.  Don't stay angry.''



He nodded.  It wasn't so easy, though.  Letting things go, relaxing, he couldn't help but feel like he'd fall apart if he did.  He couldn't get his hopes up about Panacea's willingness to help his dad – and facing any of that head on, without a buffer of smouldering fury?  It might leave him unable to serve and protect the people who really needed it.  He felt his pulse quicken a step at the thought of it.



He hedged his answer, ``I'll work on it.  Sorry if that's been bothering you.''



``It's okay.  I'm tougher than I look.''  She bumped one fist against the armor that covered her chest.



``And I'm sorry, again, for saying what I did.  You're good people, Missy.''



``Want to go back to class?'' she asked.



``If you're okay?''



She nodded.



When they returned, the Wards and Glory Girl were out in the hallway.  The PRT officers were rushing out of the room, pulling their helmets on.



``You're back,'' Weld informed them, ``Just in time.  Class is cancelled.  We've got trouble.''



\blacksquare



The scene was set up in the husk of a building.  Walls loomed on three sides, but there was no roof remaining.  The floor was uneven, composed of layers of broken boards, shattered drywall and chunks of concrete.



``There's two more crime scenes like this?'' Clockblocker asked, eyes wide.  He craned his neck upward to look above them.



``Yeah,'' Weld spoke.



``It's the middle of the day,'' Kid Win spoke, ``Broad daylight.''



Clockblocker looked at the overcast sky above.  Not quite daylight. And people weren't around.  It was still ballsy, and more than a little scary.



On each of the three interior walls of the older building was a body, twenty feet above the ground.  Each had received a different kind of treatment.  To their left was a corpse that had been flayed, the gender no longer identifiable.  Directly opposite their group was the corpse of an obese woman, charred black.  Completing the scene was the body of what appeared to be a homeless man, or one of the people who'd been rendered homeless by the recent disaster, judging by the layers of clothing he wore.  His limbs had been severed at each joint, then reconnected so each was joined by a short, foot-long length of chain.  Nails placed through the chain kept him in position, head hanging, a macabre puppet with an overlong body.  The chains jangled and swung in the wind.



Occupying the same building as the corpses was a familiar group.  Trickster, Sundancer and Ballistic stood beneath the corpses.  A winged figure that might have been a gargoyle, demon or dragon was clutching to the sides of an empty window frame with three talons, the other reaching toward the homeless man.  Genesis.



``Pardon the cliche, but this isn't what it looks like,'' Trickster spoke.



``I believe you,'' Weld spoke, ``I've read your file, and this isn't your M.O.''



``Excellent, excellent.  I commend you,'' Trickster tipped his hat, ``Then we'll be on our way?''



``No.  But if you come into custody-''



``You'll arrest us for any number of other criminal charges we've got waiting.  And you can't promise that one of your superiors won't try to stick us with the blame for this.''



Weld frowned.



``Let us go.  Whatever happened here, it deserves your full attention.  You should be trying to find and capture the \emph{real} criminals.  This guy here was still alive when we arrived.''  Trickster pointed at the man with the chain limbs.



``Can't do that.  You're still suspects, regardless of how much this deviates from your usual methods.''



``A shame,'' Trickster bowed.



In the blink of an eye, Weld disappeared, and Genesis loomed in his place, eight feet tall and nearly as broad across the shoulders, a body of pebble-like scales, heavy with muscle, a short tail and broad bat wings sprouting from her shoulders.  She spun to face the rest of the Wards as Weld fell from the window.



Ballistic turned on the fallen captain of the Wards, unloading a barrage of debris and rubble to keep the metal skinned boy off-balance and on the defensive.



Clockblocker lunged for Genesis, hand outstretched.  He was mere inches away when Genesis disappeared from in front of him.  Or, rather, Clockblocker had been moved somewhere else.  A lack of proper footing made him stumble, and he nearly collided with one of the dilapidated walls of the ruined building.



As he spun in place, catching a glimpse of Genesis exchanging blows with Glory Girl, he had his position swapped yet again.  He found himself once more with his back to the brawling pair.  One of them bumped into him, and he sprawled.  If only he'd been able to tell if it were Genesis or Glory Girl that bumped into him; had he known, he might have used his power, taken Genesis out of the fight.



\emph{Annoying}.  He climbed to his feet, wary of more teleportation hijinks.



Kid Win wheeled on the spot to raise a square-nosed pistol and fire what looked like a brilliant blue flare at Trickster, but the teleporter swapped positions with him.  Kid Win ducked the moment he was teleported, but he still got grazed by his own shot, blue sparks showering off his armored costume, small arcs of electricity dancing briefly around the metal joins.  Sundancer created her flaming ball – small, but still far too bright to look at – and sent it after Kid Win.  The young hero scrambled for cover, dropping his gun in his hurry to get away from the superheated orb.  Flechette moved to shoot, then reconsidered, threw a handful of darts at Trickster instead.  The darts disappeared in midair, and splinters of wood and small stones dropped straight out of the air where they had been.



\emph{Really fucking annoying}, Clockblocker revised his summation of the teleporter.



Shadow Stalker had positioned herself on the ragged top of the wall where the roof had crumbled away, high above the skirmish, cloak billowing.  She fired a shot at Ballistic and Sundancer, reloaded as Ballistic sent a piece of rubble flying through her shadowy form, then fired again.  The Travelers had body armor, so she wasn't doing more than distracting them.  The needles of the tranquilizer darts wouldn't pass through the durable armor or material.



``Red rover!'' Vista shouted, ``Go!''



\emph{G}\emph{ood girl}.  Clockblocker dashed for Trickster, and the distance between them compressed to a matter of feet, the highest points in the uneven ground flattening to make running easier.



Trickster swapped him with Vista, placing him several feet back.  Ahead of him, he could see the girl where he'd just been, within a few feet of the teleporter.  Clockblocker found his footing, darted forward once more.  Again, Vista's powers helped close the distance.  Kid Win, Flechette, and Vista joined him in charging the enemy, so that Clockblocker wouldn't be set too far back if he was teleported to their locations.



Sundancer moved the orb in between them and Trickster, igniting a few of the pieces of wood that were exposed and above the water.  Vista responded by raising her hand to shrink it dramatically.  Weld ducked one of Ballistic's attacks, then charged for the orb, striking it out of the air with one fist.  The blow dispersed it enough that Sundancer couldn't draw it back together, and a wave of hot air washed over everyone present.



Weld, for his part, staggered back, his hand glowing white-hot.  He flexed his glowing hand, and it moved slowly, stiffly.  Even as far down as his elbow, the metal of his arm was an orange-red.



Clockblocker didn't get a chance to see if Weld was okay.  He charged around his team leader, using the metal boy's broader body to put himself in Trickster's blind spot.  From this position, he tried to charge and tag the villain.



An instant before his hand could brush against Trickster, the villain was gone, and Weld was in front of him.  His hand touched the metal of Weld's back.



He breathed a sigh of relief when Weld turned around.  Only the fact that he'd expected something along these lines had allowed him to turn his power off in time.  Spinning around, Clockblocker reached for the space Weld had just vacated, but Trickster was already swapping places with Glory Girl to place himself as far away from the thick of the fighting as he could get.



\emph{I can't keep track of this} guy.



Clockblocker looked around to survey the situation.  His group was sandwiched between the Travelers, now.  On one side, Sundancer and Ballistic crouched in the far corner of the building.  Trickster and Genesis stood on the other side, atop the rubble that spilled across the building's entrance and onto the flooded street.



Genesis inhaled, chest expanding, and Weld was the first to react, stomping one foot hard into the rubble underfoot, using his foot to raise a large, ragged piece of plywood.  With his hands, he forced the large wooden board into a standing position, placing it between himself and Genesis.  Kid Win, Flechette and Vista wheeled on Ballistic and Sundancer.



Weld's piece of plywood served to block the worst of whatever it was that Genesis exhaled.  From what Clockblocker could see around the plywood, it was a dark, gray-black vapor.  Wisps billowed around the edge of the board and drifted their way – it had a bitter smell and taste, like ashes mixed with something foul.  Even inhaling a trace of it through the air holes of his mask forced barking coughs from his lungs.  His teammates seemed to be in rougher shape, Vista falling to her hands and knees.  The changer's exhalation hadn't even reached them directly.



\emph{So, that's what a changer nine brings to the table}.  \emph{Different forms, each with their own powers}.



Weld staggered as Genesis lunged forward, and Clockblocker ducked low under Weld's arm, planted a hand against the plywood.  He felt his power snap out to encompass the material, and he fixed it in place, cutting it off from the flow of time.



A second later, he felt a heavy hand on his shoulder.  Weld, standing over him, gave him a quick smile and an offered hand.  He returned it with the briefest of nods and took Weld's hand to stand straight.  Together, the pair of them stepped back and away, to see Genesis rising into the air with heavy flaps of her bat-like wings, inhaling to prepare another blast of the noxious smoke.



He felt\emph{ }oddly calm as his group squared off against the villains with some of the highest power ratings in Brockton Bay, beneath the grim display of the three hanging corpses.  He reached into the slot of the armor at his side and withdrew two sheaves of paper.  Moving his thumbs in one direction, he fanned out the papers, holding them like anyone else might hold a pair of knives.



He realized what it was, this calm.  Whatever else it was, this fight was a refuge from that feeling that had plagued him since the fight with Leviathan ended.  The feeling that he was always in the wrong place, doing the wrong thing at the wrong time, in the face of a city in crisis and a dying father.  This, right here, was where he was needed.  



\emph{This is what I'm here for}.





