





\emph{I'm a tinker.  I'm supposed to be smart.}



\emph{So how can I have been so stupid?}



Ballistic raised one hand and pointed at Kid Win.  He waited until Kid Win moved before kicking at the uneven, rubble-strewn ground, sending a spray of concrete and wood fragments flying like a hail of bullets.  It only grazed the teenage hero mid-leap, lacerating the side of his stomach, hip and thigh, chipping his armor.  It still hit hard enough that it twisted him in midair.  He landed on his back atop the rubble that covered the ground, grunted.



``Hey!'' Ballistic bellowed, ``Little girl!''



Kid Win saw Ballistic pointing at Vista.  The villain, between his build and armor, had the frame of a football player, a dramatic contrast to the young heroine.  He pointed at her, paused long enough for her to bend the ground into a semblance of cover, then launched a chunk of concrete at her.



The concrete flew at an angle that wouldn't have hit the girl anyways, struck the barrier and shattered, sending debris careening onto and into the girl.  Vista screamed and fell backwards, part of her barrier crumbling to land on top of her.



\emph{He's telling us exactly where he's going to attack next.}



Kid Win looked up, saw Sundancer with her orb hovering a good fifteen feet off the ground, keeping it away from the walls of the building and the corpses that were hung above them.  Even though it was fifteen feet up and thirty feet away, he could feel the heat of it prickle his exposed skin.  He knew from the Endbringer fight that she could make it bigger, move it faster.



As the burning sphere drifted forward, staying at roughly the same height, Flechette and Glory Girl were forced to scramble away.  Shadow Stalker leaped off of the top of the wall and into the alleyway next to the building to get away from the heat.  Only Vista remained where she was, caught under debris that she was striving to shrink down and push away.



It dawned on Kid Win.  Sundancer and Ballistic, at the very least, were holding back.  Because they were strong enough that going all out would leave corpses.



The revelation didn't make him feel any better.  In fact, it was just the opposite.  If these guys got desperate or panicked, they might stop being so polite about it.



Trickster and Genesis were tangling with Weld and Clockblocker – Clockblocker was putting paper in the air, freezing it to give himself footholds to go after his flying opponent.  Any time Genesis moved to attack, Clockblocker set paper in her way, edge towards her, or he tried to duck in close enough to touch her.  Giving up on more physical means, she exhaled a cloud of the choking smoke.  Clockblocker and Weld both worked together to minimize the spread of the cloud, using paper and plywood, freezing it in place with Clockblocker's power.



Kid Win decided they had a handle on that.  It was up to him to help against Ballistic and Sundancer.



As he climbed to his feet, breaking into a run before he was even standing straight, he raised his spark pistol and fired off a series of oversized blue sparks at Ballistic.



Trickster managed to teleport him again, swapping his position with Ballistic's.  The forward momentum of his sprint was enough to get him out of the way of his own gunfire.



His spark pistol sported a small power core that used spatial warping technology to magnify and then reabsorb a steady electrical current.  The barrel was wired with a helix-shaped electromagnetic rail, based on some of Armsmaster's old data on the `hard' light Purity and Dauntless created.  Nanomolecular, ionically charged rifling on the barrel's interior was arranged to guide the fired charges into a rough elliptical shape, which sustained their shape and consistency the longest.



In laymen's terminology, it was not unlike a power bar that was plugged into itself, with a small addition that made each revolution of the current larger than the one before.  An attached battery kept the current going.  The shots themselves were `hard' electricity condensed into balls, which meant they had a physical impact to them, due to how they carried and transferred kinetic energy.   Given how the weapon charged, waiting a few seconds between shots meant the next shot hit harder, up to a limit.



\emph{I can make something like this, which is brilliant, then I go and dismantle my fricking hoverboard to get parts for a project I never even finish.  Idiot.}



Ballistic marched towards Vista, who was trying to climb to her feet.  He was intercepted by Glory Girl, who slammed him into a wall.  She punched him, drove her knee into his gut, then slammed him against the wall again, to keep him off-balance and hurting.



Ballistic slumped against her and grabbed at the collar of her costume for support.  A second later, Glory Girl was a blur, disappearing into the skyline.  His attacker gone, Ballistic fell onto his hands and knees with a grunt.



Flechette threw a handful of darts at Sundancer, pinning the girl against the wall.  Somehow Flechette had avoided Trickster's attention.  How?  Kid Win turned to look, saw that she was standing so her body blocked Trickster's line of sight to both the darts and his teammate.



\emph{So he can only teleport what he sees?}



Kid Win moved to mimic Flechette's technique, running to a position where he would be between the injured Ballistic and Trickster.  He cocked his spark pistol.



He was nearly lined up for his shot when his gun disappeared from his hand, an awkwardly sized piece of wood taking its place.  A second later, his mask and visor cracked against a hard surface.  He had to grip the wall to steady himself and keep from falling.  He'd been teleported.



Then the wall moved beneath his hand, and he heard Clockblocker shout, ``Get down, Kid!''



He let himself fall, simultaneously realizing he had been leaning against Genesis, in her gargoyle-like form.  Weld slammed into the villainess, his left hand in the form of a heavy miner's pick.  It did a surprising amount of damage, but she didn't seem to care.  She gripped Weld around the face with a claw, raked his chest twice with criss-crossing slashes of her other hand, leaving deep gouges in the metal.  The same noxious black smoke that she had been breathing began to billow out of the hole the pick had made in her chest.



Clockblocker charged, but Genesis shoved Weld so the two heroes stumbled into one another, delaying them long enough for her to leap into the air.  She beat her wings to keep herself aloft and out of reach.



Kid Win unslung his laser rifle and fired at the villainess.  His first shot grazed her, as one flap of her wings carried her higher into the air, but the next two hit the mark.  One struck her in the shoulder, leaving a hole large enough to fit his hand through, the other struck her in the side of the head, doing a similar amount of damage.



Genesis dropped from the sky, exploded into a mess of dark smoke and pebbles as she struck the ground.



Feeling a moment's panic, he checked the settings on his gun.  Normal levels, no anomalies.  It could heat metal and other inorganic materials, cut through more fragile materials, but against a person, it wouldn't do more than hurt and maybe leave the mildest kind of burn.



\emph{That's her power}, he reminded himself, \emph{you didn't kill her.}



But his gun\emph{ had} done a surprising amount of damage.  Was it some interaction with how she pulled her new shapes together?  A specific wavelength, a weakness to lasers?



He wasn't about to complain.  He wheeled around, fired on the other villains.



An injured Ballistic opened fire on Vista, discharging a series of pieces of rubble at an angle.  It struck the ground just in front of the girl and fallout from the impacts showered her.  Each shot drove her back further, buying him a chance to limp to Sundancer's side.  He touched the darts that were fixing her to the wall, sending them flying into Weld's face.



``Fuck!'' Weld cursed, the metal spikes of the darts jutting out of his jaw, cheekbone, eyebrow and forehead, ``Takes forever to get my face right after something like this!''



Trickster's teleportations had placed the enemy's group in the interior of the building, with the Wards surrounding them.



Surrounding one's enemy wasn't quite an advantage when the enemy could teleport, but for a moment, they all paused where they were, various weapons at the ready.  It was the kind of momentary peace that fell when everyone was waiting to react to what the others were doing.



A wind blew past them, and Kid Win blinked as a fat droplet of water spattered against his visor.  It was starting to drizzle.  He glanced up at the corpses where they hung on the walls of the building.



``The water's going to wash away the evidence if you don't let us go and hurry to check on the bodies,'' Trickster spoke.



``Crime scene techs can't get here in time with the roads like they are,'' Weld spoke.  ``And we're not allowed to touch the evidence anyways.  Rules.''



``Rules?  You shouldn't sweat those things so much,'' Trickster chuckled, ``Here, I'll help you out.''



Weld disappeared, and the burned corpse flopped to the ground.



``Shit!'' Clockblocker shouted, running forward.



Weld dropped from the wall for the second time in a matter of minutes as the restraints intended for the woman's corpse tore free of the concrete.  Vista reshaped the wall to ease his descent.  Kid Win raised his laser rifle to fire at Trickster.



\emph{Dumb}.  He regretted it the second his finger left the trigger.



As he predicted, he found himself somewhere else in the blink of an eye, and the impact of his own gunfire slammed into his back, intensely hot.  He threw himself to the ground at the base of the building, where water pooled, rolling so his back was submerged.



\emph{It's not lethal, can't do any permanent harm, you had it vetted, tested on pig meat.}



The balance of the fight had abruptly shifted.  Clockblocker, Flechette and Vista were where the three Travelers had been, and vice versa.



``Nuh uh uh, kiddo,'' Trickster spoke, as the gap in the wall began closing behind his group, ``Up you go.''



The flayed corpse appeared in Vista's position.



\emph{No!  }Kid Win turned, saw Vista on the wall.  She'd gotten tangled in the loops of wire that had been holding the corpse up.  The metal wire was coiled around a shattered part of the wall, and more than one wire had caught around her neck.  Another looping of wire bound her body, one of her arms caught against her side.  She struggled to pull at the wire on her neck with her free hand, but it was little help.  The wire pulled so tightly against her throat that Kid Win feared it would cut her skin.



``Trickster!'' Sundancer cried out, horrified.



``Just run!'' was the villain's only reply.  The three villains started running, leaving the building behind, their footsteps sloshing and splashing.



Kid Win raised his laser pistol, aimed carefully, then fired, landing the shot a half-foot to the right of Vista's throat.  The wires heated and split, freeing her, and she dropped a foot before catching on more wires.  Nothing dangerous, this time, but it was a fair distance to fall and one slip could see her getting cut on the wire, strangled or cracking her head open as she fell.



Shadow Stalker materialized behind Trickster, catching him around the throat in a headlock.  She used one foot to kick his feet out from under him, and then forced him face first into the water.



Kid Win hesitated.  \emph{Help her or help Vista?}



\emph{Vista}.  Shadow Stalker would say she could handle herself.  Made a point of trying to.



He fired more shots to free Vista, missing the wires one or two times.  The heroine, for her part, focused on angling the wall beneath her to allow herself to slide down instead of falling the full distance.



Ballistic shot Shadow Stalker, driving her back.  The attack had left a gaping hole just below her heart, the edges wispy.  The gap closed, but the attack had separated her from Trickster, and hurt her badly enough that she crumpled to the ground, a hand to her chest.



Kid Win fired a salvo at the retreating villains, grazed Ballistic.  Sundancer turned, directing her orb between their groups.  She dropped it into the water.  Massive clouds of heated steam rose where the orb met water, obscuring the battlefield.



By the time it cleared, the villains were gone.



It took a minute to check that none of them had suffered any permanent damage.  After some debate, they moved the bodies to a more secure, dry spot, inside the building. Glory Girl managed to make her way back two minutes after the Travelers were gone, helped with the last body that still hung on the wall.  By the time they were done, the rain was pouring down.



Kid Win stared down at the corpses, an ugly feeling in his gut.



He \emph{was} dumb, easily distracted, prone to leaving his projects unfinished, and it was moments like this that this knowledge hit him particularly hard.  His dad had made him get tested, and the doctors had labeled him with ADD and dyscalculia.  He held to the opinion that the ADD diagnosis was way overused – he liked to think that he was just a daydreamer, prone to getting lost in his thoughts.



The dyscalculia was something concrete that he couldn't deny or explain away.  He couldn't keep numbers in his head, couldn't make the most basic intuitive leaps or connections with them.



All of that had been before he got his powers.  Nothing had changed, except that now he could visualize something, instinctively know how he could put it together.  His disability or disabilities put him a step behind the rest.  His daydreaming was worse, because his thoughts were so damn \emph{interesting}, now.  He couldn't take reliable measurements without using computers to do it.  Couldn't finish half his projects without feeling compelled to move on to something else.



The PRT staff insisted he was exceptional with antigrav and guns, had it even marked in his file, but he knew it wasn't so true.  He finished his guns because they were \emph{simple}, in their own way.  It was easy enough to take three half-finished gun projects and mash them together.  Create something with multiple settings, even.  As far as he was aware, he was the only Tinker in the PRT's records that didn't have a defined specialty, gimmick or trick.  He was increasingly worried that his special talent as a tinker was being able to occasionally make something despite his learning disability.  Which would suck, if it were true.



There were exceptions.  He'd finished bigger projects.  His hoverboard, driven by the idea of how awesome it would be to fly.  Even then, it had been a chore.  Monumentally stupid of him to dismantle it.  The \emph{idea} and motivation driving the action had been good: he was graduating the Wards in a little while, he'd be expected to change his name and adjust his methods, because an adult calling himself \emph{Kid} Win was lame.  He'd had an idea about a harness with a floating array of turrets that could fire different munitions depending on what gun he holstered in the main slot.  Self adjusting and adaptive the way his Alternator Cannon was.  Except he'd gotten frustrated at a snag in the testing, put it down to take a break and hadn't picked it up again in six days.  His hoverboard had effectively been destroyed for no reason, when it might have made the difference in getting the Travelers into custody.



His Alternator Cannon was the real gem.  It had been the result of a medication the PRT's doctor had prescribed, which he'd been forced to stop after two weeks when he began to get increasingly dizzy, anxious and nauseous.  While he'd been taking the pills, he'd been focused, had a glimpse, maybe, of what he could do if it weren't for his distractibility and daydreaming.  When Piggy had spoken of destroying the thing, the mere thought had been crushing.  Then Leviathan had destroyed it for real, maybe the only truly brilliant thing he'd be able to make.  He harbored fears it might even the only brilliant thing he'd \emph{ever} be able to make.



He wasn't the worst hero ever, he knew that.  He had things he could do.  He could let the worries and the dozens of unfinished projects alone, most days.  That changed when his team got thrashed.  Thoughts like that had been plaguing him since the Endbringer event a week ago.  He couldn't shake the notion that he was in the running for the weakest member of the team.  The notion that he was dumb, second-rate.  That this loss, here, was his fault, because he had dropped the ball. \emph{ The people of this city deserve a better hero, a more focused one}.



Weld spoke, disturbing him from his thoughts, ``I just got a message.  PRT is on their way.  We head back now.''



Hearing the unenthusiastic replies of his teammates, Kid Win realized that the rest of the team wasn't in any better of a mood than he was.  Losing had a way of doing that.



Strangely comforting.



\sectionbreak



``Got word from the Protectorate.  They're handling the case with the bodies, we're not to touch it or get involved in any way,'' Weld spoke, folding his arms.  He had what looked like acne – blisters of extra-shiny metal on his face where the remainder of the darts hadn't yet been fully integrated into his `skin'.  He reclined in an expensive, custom-made office chair, capable of supporting his dense, heavy body.  Everyone else had found seats in the central room of their headquarters.  Everyone, that was, except for Glory Girl, who had gone home.  She wasn't yet an official member of the team.



``No word on what's going on?'' Clockblocker asked.



``They're staying quiet on the subject,'' Weld spoke.



Vista leaned forward, ``Maybe a serial killer?''



``We should focus on what we do know,'' Weld shook his head. ``As far as tonight's patrols-``



``Actually,'' Kid Win cut in, ``Sorry.  But I have one theory.''



``What?'' Clockblocker asked.



Kid Win glanced at Weld, checking to see if their leader was ok with it.  Weld didn't say anything, which he took as assent to continue.



``There were two other crime scenes, right?  Any idea if there were the same number of bodies at each crime scene?''



``Same number--'' Weld raised an eyebrow, ``Why\ldots Oh.  \emph{Shit}.  I think I follow.''



\emph{Smarter than you'd think, given his brute-force power and his appearance}, Kid Win realized.  \emph{Or I'm just that bad with numbers.  The connection took me twenty minutes to make.}



``Three crime scenes with three bodies each.  So it'd be nine bodies?'' Clockblocker asked, ``Each killed in some different way?  I don't see what killer that would fit with.''



``Not one killer,'' Kid Win answered, ``Nine bodies, each for different killers.''



``The Slaughterhouse Nine,'' Clockblocker leaned back in his seat, groaning, ``Fuck, that'd be all we needed.''



``Wouldn't be the first time they've arrived at a location in the wake of an Endbringer event,'' Flechette pointed out.



``Maybe it's them,'' Weld conceded, ``And \emph{maybe} the Protectorate figured that much out, with the clues they have from the other two scenes.  It could be someone or something else.  Either way, it's not our case, not even in our league, and we should stay as hands off as we can manage.  We need to talk about patrols and tonight's duties.''



``The grunt work,'' Flechette offered a literal grunt to punctuate the statement.  Kid Win and Clockblocker chuckled.



``Vista's due for a patrol, and as a young member, she has to go with someone.  Lily?''



Flechette smiled a little, ``Quick to make me pay for the snark, huh?  No, it's cool, I've been wanting a chance to shoot the shit with Vista.''  She extended her fist, with index finger and thumb extended to form a gun, mock fired it at her junior teammate.  Vista rolled her eyes.



``Clockblocker, you and I will handle the night's shifts after that.  Your call if you want to patrol with me or not, we can cover different routes and go for a wider area if you'd rather.''



``Alright.  We'll figure it out.''



``Leaving Shadow Stalker.  You okay with the late-night, Sophia?''



``Yeah, fine,'' Sophia didn't look up from her laptop.



``And me?'' Kid Win asked.



``Special duty, tonight,'' Weld smiled, ``You're recruiting.''



``Recruiting?''



``There's a kid calling himself Chariot.  Been racing around the city with a powered suit that lets him move a hundred miles an hour.  Assault finally caught up with him last night, brought him into custody.  Wound up calling the kid's mom, got him to agree to talk to our recruiter.  You.  You'll be meeting the kid in his home.''



``Why me?''



``Shared interests.  You're both tinkers.  You have the best idea of how he thinks.''



Kid Win nodded.  He couldn't quite put his finger on what he was feeling.  A measure of excitement at the idea of getting to talk to another tinker that wasn't Armsmaster?  Sure.  Fear?  Would he be replaced by a new tinker?  It was an immature thing to be spooked about, he knew that, but that didn't make it any less real.



``Cool,'' he spoke, by way of agreement.



``You convince him, it'll look good to the guys upstairs,'' Weld informed him.



Right.  \emph{Great.  }\emph{Pressure}.



``Now, onto a more serious topic.  I'm seeing that this team is really disorganized, these days.  I have no problem handling the brunt of the paperwork, it gives me a degree of insight into what's going on that the files don't.  I don't even mind cleaning up the kitchen and showers here when the janitors are off duty.  But we really need to \emph{communicate}.  Last night Flechette went on patrol and ran into a situation with Parian she should have been briefed on.  It could have turned hostile.''



``Sorry,'' Vista muttered.



``It turned out okay,'' Flechette smiled a little.



``Right.  It's \emph{okay}, it's understandable, given all we're trying to handle,'' Weld reassured her, ``But we can't miss out on details and updates on the overall situation.  The Protectorate have their hands full with the gang wars between Fenrir's Chosen, Purity's group and Coil,  they're now dealing with this serial killer or serial killer\emph{s}, and they're \emph{still} updating the records.  So here's what we're going to do, I've checked it with Piggot, she agrees.  I'm picking up an extra patrol shift, and I'll be adjusting your patrol shifts down by twenty minutes each, moving them around slightly.  With the downtime that creates, we're going to have meetings like this, every day.''



Pausing, Weld glanced at Clockblocker, as if expecting a response.  When Clockblocker only nodded assent, Weld's eyebrows rose a fraction in surprise.  He continued, ``Gives us a chance to talk about our recent patrols, fears, concerns, ideas.  Or hell, just talk, because I'm seeing this trend where we only see each other in passing, while patrolling or in class, and some of you are going out of your way to spend time together and hash stuff out, even at the detriment of stuff like school.''



``You're talking about class, earlier,'' Clockblocker said.



``More or less.  Not saying it's a bad thing, but we can restructure our schedules, make time for it, instead of detracting from an area we need to pay attention to.''



``Sure,'' Clockblocker agreed.  Was there a note of irritation in his voice?  Kid Win couldn't tell.  Dennis was playing along, at least.



``Now, about the paperwork you guys have been submitting, there's been a few recurring problems\ldots''



Kid Win sighed and settled into his seat.  This was going to be a little while.



\sectionbreak



The building was ugly, had trash piled up on either side of the front door, a sour smell wafting out from it.  The water level wasn't so bad here, and the building was almost entirely intact.  The only sign of damage was the boarded up windows on the first and second floors where the glass had been knocked out of the window frames.  Red brick, it seemed like the usual sort of tenement building one would find in the Docks.



He stepped inside.  A Hispanic boy in the front hall whistled sharply as Kid Win stepped inside, while a group of Asian-American boys and girls in dirty clothing ran around him, screaming at a ear-piercing volume as they continued a game, some pointing and hooting at the superhero.  Occupants aside, it was dark, with only two dingy lightbulbs and no open windows.



\emph{It's nine o'clock at night.  Don't these kids have a bedtime?}



He checked the folded paper he had in his hand, found the room number, and headed up the stairs.  A morbidly obese, older man sat halfway up the stairs, maybe a babysitter for the kids.  Kid Win \emph{hoped} the man was a babysitter, because the man was white and the kids weren't, meaning he probably wasn't family.  If he wasn't getting paid, there was only one uncomfortable explanation for why the man would be willing to tolerate that yelling and squealing.



\emph{Or maybe he's deaf}.  \emph{Let's go with that.}



The fat old man didn't budge an inch as Kid Win approached, forcing the boy to squeeze by.  He made his way up, ignored a gang of fit twenty-something Asian guys who were standing guard in the hallway on the second floor.  On the third floor, he headed past people who were sleeping on blankets in the hallway, found apartment 306.



The door opened a second after he knocked.  A tired looking Hispanic woman greeted him, ``You're the superhero, I take it?''



``Yes.  Kid Win,'' he extended his hand.  She shook it firmly.



``Ashley Medina.  My son's back through here.''



There was a sense of pride in the narrow apartment, Kid Win saw.  An undercurrent of aesthetic taste, matching knick-knacks and furniture.   There were marks of a vacuum cleaner's recent run over the carpet and both kitchen counters and dining room table were immaculately clean in a way that suggested she'd gone to some effort to clean up.  In a building like this, though, there was only so much you could do.  There was a water stain on the ceiling, dark brown marks on the carpet under a small rug, maybe from a previous occupant.



``If you'll wait here, I'll get him.''



Kid Win sat on the sofa.  He noticed the cathode ray tube television was missing its screen, had been gutted.  Quite likely for parts.  The toaster was a goner, too.  Only the wireless modem in the corner of the kitchen had survived, green lights blinking.



\emph{He has priorities, at least}, Kid Win thought, with mild amusement.  \emph{Gotta have an internet connection.}



When Chariot arrived, Kid Win stood, offered a hand.  There was a delay before the kid shook it.  He was lanky, with big ears and close shorn hair that made him look slightly goofy, but he had a wary look in his eye.  He wore a t-shirt and jeans that were stained with grease, had lots of little cuts and stains on his fingers, hands and forearms.



\emph{Been there}.  \emph{Substandard tools, not enough parts.  I can use that}.



``Please sit,'' Chariot's mother said.



Kid Win obliged.  Chariot was the last to take a seat.  Was he reluctant, something else?



``Chariot, is it?''  Kid Win ventured.  \emph{God, hope I don't fuck this up.}



``Mm,'' was the noncommital reply.



``Just to give me an idea, on a scale of one to ten, how interested are you, in maybe joining the Wards?''



``Ten's high?''



``Ten's a lot of interest.''



``Four.''



``Trevor!'' Chariot's mom admonished, ``They offer funding, education-``



``We do,'' Kid Win interrupted.  \emph{If mom pushes, this guy's only going to }get less interested.  \emph{Shit, a four is low.  }\emph{Maybe if I do the talking\ldots} ``It's good money, with room for better money.  \emph{Especially} for a tinker like you or me.''



``How's that?''



``The guys in charge want tinkers.  They \emph{really} want tinkers, both because they want us in a position where we won't be making trouble for them, and because and they want the kind of stuff we can create.''



``I'm not giving up my stuff.''



Kid Win paused.  \emph{This is like looking into a mirror to a year and a half ago}.  ``Look, I can see your TV, your toaster.  Chances are you've gone to the Trainyard or a scrapyard to find some stuff.  Old batteries, car parts, chains, good metal, whatever.''



``He wanted to go to the Trainyard,'' Chariot's mother cut in, ``I told him no, caught him trying to sneak out.''



Chariot scowled a little, looked away.



\emph{This would be easier without her here}.  ``I get it.  Been there.  You're hungry to use your power, but more than any other kind of cape, you're facing a hurdle in terms of the entry-level resources you need.  This is where the team would support you.  You get funding, a \emph{lot} of funding, to put your stuff together.''



Kid Win reached into his belt, retrieved a compact disc.  He placed it on the glass coffee table, then withdrew a set of small tools from the other side of his belt.  He dismantled the object and began laying out the components one by one.



Chariot reached for the nearest component, and Kid Win moved to block the boy's hand.  ``Don't touch, please.  Look only.  Trace oils and static charge could damage something.''



The boy gave him an annoyed glance, bent over the table to look closer at the chips.



``What's this crystal?''  Chariot asked.



``3D computer chip.  Uses light instead of electrical current.  They're made by this Protectorate tinker down in Texas.  She gets funding to produce a set number every month, in addition to her regular pay.  So long as you're in the program, you can put in an order for her stuff, with the specs you want.''



``And this metal threading, gold?''



``Gold, for maximum conductibility.''



``That's a camera, this would be the power source, that part does something with wavelengths, and this reads energy\ldots but I'm not getting it.  What does this do?''



Kid Win quickly slipped the pieces back together, turned the compact device over, then pulled out his smartphone.  Touching the screen, he activated the compact device.  It floated above the coffee table.  He turned his smartphone around to show them the image it was streaming from the device's camera.



``So much effort, for a video camera?'' Chariot's mother commented, ``My tax dollars are going towards this?''



The dumbfounded look Chariot gave his mother put Kid Win in the awkward spot of having to suppress a smile.  \emph{This is a point for me.  If I asked him again, what would he say?  Five, six?}



``You join the Wards, you get exactly what you need to reach your full potential as a Tinker.''  \emph{A small lie there.  Not like I've reached my full potential}.  ``And anything you make, the PRT buys the rights from you.  If you're willing to give up that much, you can do well for yourself.''



``You're talking money?'' That had piqued Chariot's interest.  He leaned forward, elbows on his knees.



``I maybe shouldn't, but I'm going to tell you what I'm getting out of it, because it's almost definitely going to be the exact same for you.  I get paid, but the money goes straight into a trust.  I've made enough to pay for my college education, and every dollar I earn beyond that is going to be waiting for me as a cash award, if and when I graduate from a four-year postsecondary program.  I'm getting four hundred dollars in allowance each month, just to mess around in my workshop, all my materials are paid for, and I currently have about two thousand dollars sitting in the bank, right now, from that.  Once I turn eighteen?  I make \emph{more}.  It automatically transitions to a job with good pay, working with the Protectorate, and the hours will be totally flexible around any classes I take.''



``But he's risking his life,'' Chariot's mother spoke.  Chariot frowned.



``He is.  There are responsibilities.  But honestly?  There's zero way he's going to be able to go out and try out any of the stuff he's made without running into trouble.  People are going to pick fights, just because he has powers.  If he tries to hang out in a workshop he establishes on his own, they're going to find him, strong-arm him into putting something together for them.  Not just villains, either.  Heroes too.  Being a tinker doesn't just make you a target.  It makes you a resource.  It's why pretty much every tinker out there is a member of a larger, more powerful team.''



``Then Trevor could just not use his powers?'' she spoke.



``Sure,'' Kid Win folded his arms, leaning back against the back of the couch.  ``What do you think, Chariot?  You think you could keep from using that power of yours?  Be normal?''



Chariot frowned, looked down at his scratched-up hands, ``No.''



Kid Win nodded in agreement, ``It's a part of you, Chariot, a part of how you think, now.  I'm telling you this is the best option.  The safest.  Having a team means you're protected, free to do what you \emph{need} to do.''



Chariot's expression indicated clear interest.  Then he frowned, ``I don't want to give up my stuff to others.  It's mine.''



Something struck Kid Win as off about the reply.  What was it?   It was out of tune with the flow of the conversation, didn't quite match up with Kid Win's own experiences being recruited.  Maybe it sounded forced?  But why would Chariot fake reluctance?



He pushed forward, anyways, ``I get that, really.  But it's only given away in name.  You still get to use it, you just can't give it away or sell it to others.  The benefit is that you gain access to all the stuff and plans \emph{other} PRT tinkers have made.  I can't show you any more of that than I have, but the fact is, you'd be able to look at my blueprints as easily as I could look up yours, get inspiration\ldots



``\ldotsOr you could look at the sort of stuff \emph{Dragon makes}.''



Chariot's eyes lit up.



``Tell me you're not interested, now.''



``I'm\ldots kind of interested.''



Again, that vibe.  Pretending he's not as interested as he is.



``They can't force you to join, but they do want you on the team.  There's no negotiating.  You'd get the same I get, pretty much, so if you're holding back or trying to fake like you don't want to join when you do, you're just wasting your time and mine.''



``I'm not,'' Chariot replied, defensive.  ``It's only\ldots this is a big deal.''



``It is.  So take my card.  Call me if you have any questions, or if you want me to pass on word that you're joining the team.''



Kid Win fished in his belt and then handed his card to the boy.  Black with white lettering and his starburst-gun emblem on the back.



``Okay,'' Chariot replied.



``Talk it over with your mom.  Get back to us.''



``Thank you,'' Chariot's mother spoke, standing.  Kid Win stood as well.  He shook her hand again.



``Not a problem,'' Kid Win replied.  He punched the boy lightly on the shoulder as he stood, ``Join.  It'd be good to talk shop with someone else that gets this stuff.''



Chariot nodded.



The mother led Kid Win to the door, and he headed out the building – the fat man from the stairwell was gone, and only the Hispanic boy by the front door was still in the hallway.  Kid Win stepped outside.



\emph{Something's off with this scenario.}



He tapped his foot a second, then stepped around the building and into the alleyway.  He retrieved his smartphone, and used it to send the hovering camera up to the third floor, checked in the windows where the apartment would be.  The boy was leaving the bathroom, going into his room.  Kid Win moved the camera to the next window over, the boy was sitting down at his computer, turning it on.



\emph{Straight to the computer.  Hm.  }Kid Win pocketed the hovering camera, then turned his attention to the smartphone.  According to the phone, there were three wireless modems in the building.  One was named with a string of violent swear words, the other was on its default settings.  Both were unlocked.  He chose the third, locked connection, clicked a button on the screen to have his phone decrypt the password.



Fifteen seconds later, he could see someone online.  Kid Win watched the white text scroll by with details on the connection's activity.



Google docs – pages of technical stuff, the boy was adding notes on gold wiring, shortform notes on antigravity, 3D crystals.  The next page the boy visited, five minutes later, was an email account.



Twenty seconds later, an email was sent.



To: C1298475739@cryptmail.com



Guy from wards came.  I'm in.



Kid Win stared at the screen for a long while.  Cryptmail.  That wouldn't be an agreement with the PRT.



``So someone got to you before we did,'' he muttered to himself.  He tapped the armor over his ear twice to open a communications channel, ``Console?''



``Weld here, manning the console.''



``Do me a favor, call everyone back to the base for a quick meeting?  And maybe call Piggot?''





