
``Don't cross the yellow line,'' Flechette spoke.



``Right,'' Vista agreed, ``I got the message the last time I came this way.''



Flechette leaned forward, found a string, beaded with water from the rain.  She plucked it twice.



Parian sloshed out from a nearby alley.  A nine-foot tall rabbit with an eyepatch and boxing gloves followed a few feet behind her, moving on two legs, swaggering forward like it had a chip on its shoulder.



``It's cute!'' Vista smiled.



``Hi Vista,'' Parian greeted her.  ``Hi Flechette.''



``Hey,'' Flechette smiled, ``We come bearing gifts.''



Vista stepped forward and held out a shopping bag, ``A dozen gallons of water, some rice, some tins of beans, multivitamins and first aid supplies.  My power will wear off pretty soon, so get the bag somewhere safe before then.''



``It's basic stuff,'' Flechette said, ``But it'll hold you for a little while.''



``Thank you,'' Parian spoke, reaching over the makeshift yellow line for the bag.  She held it behind her back with both hands.  Just over her right shoulder, cloth formed into a rough shape, a trio of needles with attached spools of thread weaving in and around it, a razor cutting at pieces of it.



``How are you managing?''  Flechette asked.



``Some kids came through around noon, roughed up the mother of one of my friends.''



``I told you to call me if there was trouble!''



``I handled it.  Kind of.  They ran when they saw my rabbit.  According to my friend's mom, they were trying to get someone to tell them where they could get food, and she was afraid they'd take everything if she told them where we have our stuff.  I think they were more hungry than dangerous.  Not enough food going around.''  The cloth took on a rough shape with arms and legs.  ``Erm, that makes it sound like I'm blaming you guys--''



``You're right,'' Flechette interrupted.  ``We're not doing a good job of getting supplies to everyone.  We can't.  Any time we try to distribute it, a group like Hookwolf's gang or the Merchants try to seize it.  Even if the heroes on duty fend them off, the citizens get scared away.''



``I suppose we're lucky to have this haven, here.  So far.  I dunno how long before someone I can't scare off comes through.''



``You have my number.''



Vista turned away as a third voice sounded in her ear.  She stepped away from the conversation, shook her head a little to shake off the water that the steady rain was depositing on her.



Vista squeezed the earbud, ``Sorry?  I didn't catch that?''



``Weld here.  Kid Win has something to report, asked everyone to come in.  Can you make it back here quickly?''



``Okay.''



She hurried back to Flechette's side and waited a few seconds for a break in the conversation.  When none was forthcoming, she put a hand on Flechette's arm.



``What's up?''



``Weld wants us back asap.''



A look of disappointment crossed Flechette's face.



``I'll see you later?'' Parian asked.



``I'll stop by later, unless I'm done with patrols for the night,'' Flechette shrugged.



``I'll look forward to it,'' Parian replied. She turned to Vista, ``Here.''



Vista accepted her gift.  A stuffed rabbit, made in the last-minute or so.  It was finely detailed, wearing a fancy dress with lace trim.  The fur had a softness that indicated high quality material, despite being wet.  She would have been delighted with the gift, were she four years younger.



It was still a really nice gesture.



She suppressed her annoyance at the child's gift and offered a smile instead, ``Thank you, Parian.''



``Let's go,'' Flechette spoke, ``Back to headquarters?''



``Back to headquarters.  Come on, we'll take my shortcut.''



They walked two blocks east to reach Lord street.  Beneath the water's surface, they could see a fissure that ran down the center of the road, zig-zagging from one lane to the other.



Vista stepped out into the middle of the road at the edge of the fissure, then concentrated.  She felt her power extend to every solid object in front of her, formed a map in her head.  There was nobody out there, which made it easier.  Slowly, carefully, she began adjusting.  She truncated the length of Lord street, then did it again, repeating the process to make the four lane road shorter and shorter.  The fissure down the center of the road squeezed against itself like a compressed spring.



``This is disorienting,'' Flechette spoke, as she gazed at the scene.  ``My power gives me a grasp of angles\ldots and I'm worried I might have a seizure if I try to use it to get a sense of what's happening here.''



``It's not that complicated.  Everything's like wet clay, and I'm smudging it around.''



Vista deemed her work done, started walking forward.  Flechette followed, eyeing the distorted sidewalk at the edges of the effect.



``You're powerful, kiddo,'' Flechette said.



``Kinda.''



``You could be one of the top dogs in the Protectorate, in five or six more years.''



Vista frowned, ``They said the same thing about Dauntless.''



``One of the Protectorate members who got killed, if I remember right?''



Vista nodded.



Flechette frowned, ``That's\ldots unexpectedly dark, coming from you.  Where did that come from?''



``What we do is dangerous.  Sometimes we die.  I don't see why I should worry about what happens five years from now when I might not even be here.''



``Are you having second thoughts about being on the team?''



Vista gave Flechette a look, ``No.  Not in the slightest.''



``But if you're concerned about risking your life\ldots''



``I didn't say I was concerned,'' Vista said, a note of exasperation in her voice, ``Just that, hey, it might happen.  I'm being realistic.''



``I can't tell if you're being amazingly mature about the topic of death or if I should be really concerned about you.''



``\emph{Amazingly} mature?''



They had reached the PRT building.  A trip that had taken them thirty minutes on the way out had taken them four on the way back, with the aid of Vista's power.  Flechette held the bulletproof glass door open, raised a hand in greeting to the PRT uniform who stood alert on the other side.  ``You know what I mean.''



Vista had to bite her tongue. Pointing out that people were being condescending had a way of making her look petulant, which only compounded the problem.  \emph{Yes.  Because any maturity on my part is something special. Doesn't matter that I have nine months of seniority over Kid Win, being thirteen means everyone expects me to be squealing over Justin Bieber or the Maggie Holt books, or dressing in pink or--}



Her train of thought stopped dead when her eye fell on the portraits on the wall above the front desk.



Three feet high and two feet wide, the two pictures were black and white, bordered by foot-wide black frames.  The pictures themselves were head-and-shoulders shots of Aegis and Gallant, both in costume, masks on.  She knew from her own experience that the pictures would have been taken in their first week on the team.  Gallant looked so young.  He had still been so young when the tidal wave had smashed into him and caved in his chest.  Only seventeen.



She looked at her own picture.  In contrast to the boys', it was vibrant, filled with color.  Her eyes, costume and the frame of the picture were a high-saturation blue-green, the background of the image a sunset orange to highlight her blonde hair.  Vista was young in that picture too.  Her photo had a missing fang tooth on the bottom row, which created a small, dark gap in her awkward smile.  She'd been just a month shy of turning eleven, then.



She \emph{hated} that picture.



She hated it all the more because she couldn't help but wonder if the time would come when that picture would be hanging over the front desk in black and white, smiling that guileless goofy smile that was everything she \emph{didn't} want people to remember about her.



Hell, were they even doing Gallant justice?  The guy who'd set out to be the literal knight in shining armor, lived his life with more chivalry than any five people you plucked off the street?  All he got was a photo and a name on a memorial.



``You okay?'' Flechette asked.



Vista tore her eyes from the portraits, ``I'm fine.  Let's go, Weld's waiting.''



Without waiting for Flechette, she marched for the elevator.  Flechette fell in step behind her.



Everyone else was sitting in the meeting room, except for Director Piggot, who stood with her arms folded.



``Thank you for being prompt,'' Piggot spoke, ``Would you please have a seat?''



Vista obediently sat in the chair closest to her.  Flechette found a chair beside Weld.



``Kid Win?'' Piggot prompted.



``Here's the deal, guys.  I went out to talk to Chariot, and there's a bit of a complication.''  He tapped the screen of his smartphone, and the computer screen at one end of the table changed to show text from a series of emails.  ``Chariot hasn't yet agreed to join the team, but there's evidence that he fully intends to join as a mole for an unknown party.''



``This evidence was assumed using legal methods, of course,'' Piggot spoke.



``Of course,'' Kid Win grinned in a way that left no doubt for anyone present that he was lying through his teeth.  ``We believe this unknown party is Coil.  There's no other criminals in town that would really do this.  Fenrir's Chosen aren't that subtle, and they're too racist to work with Chariot.  Purity's group is, again, too racist.  The Undersiders aren't well-funded enough.  It doesn't fit the Travelers' MO.''



``That,'' Piggot spoke, ``And there are prior cases of Coil using undercover operatives.''



``Prior cases?'' Weld asked.



``This doesn't leave this room,'' Piggot spoke.  Vista nodded alongside everyone else.  ``We know there are three agents employed in this very building who are working for Coil.''



``Seriously?'' Clockblocker asked.  ``As in, right now?''



``Yes,'' Piggot nodded, ``We might have gone entirely unaware, but Dragon found that one face on our security camera footage matched up with that of a known soldier of fortune.  On investigation, we found two more.  Capable gunmen, each with a wide array of skills ranging from facility with computers to multiple languages.  Very much the type Coil would employ.  We might have arrested them, but I spoke with people with higher credentials and clearance than myself, and we came to the unanimous agreement that it would be ideal to keep those mercenaries employed here.  It allows us to keep a close eye on them for knowledge we could use, and we occasionally feed them bad or misleading information, obviously with a great deal of consideration each time.''



``Which brings me to the primary subject of this meeting,'' Piggot informed them.  ``I would like to do the very same thing here, with Chariot.  He would work alongside you, quite likely see you unmasked.  You would socialize with him, and you would pretend not to know that he is passing on information to his employer.  For that, for the risks you would be undertaking, I require your express permission.''



Kid Win whistled.



``Dealing with the relationships between team members is difficult enough to begin with,'' Weld spoke, ``And you want to add this into the mix?''



``I wouldn't ask you to do it if I didn't think you could handle it.''



``What if we say no?'' Clockblocker asked.



``If only one or two of you disagreed, out of fear of your civilian identities being used against you, I would propose splitting up your team's schedules so you did not share any shifts with Chariot.  Ideally this would coincide with each of you returning to school, so your busy schedules could serve as sufficient excuse for why you do not cross paths with the boy.  Given how complicated this becomes, I would \emph{much prefer} that all of you were onboard.''



``I have no problem with it,'' Weld spoke, ``But I have no secret identity, no friends or family here to watch out for.  I totally, one hundred percent understand if anyone else has objections.''



``Not a local or a long term member of the team, here,'' Flechette said, ``My vote probably shouldn't count, but I'm okay with it, if it's what the PRT needs to do.''



``Good,'' Piggot spoke, ``And the rest of you?''



Shadow Stalker was next to agree, followed by Kid Win, Vista and then a reluctant Clockblocker.



Piggot offered them a rare smile, ``Good.  For your information, the earpiece communication channel, the computers at this console, the spare laptops and the spare smartphones will all be continually monitored by a team upstairs.  Your own laptops and smartphones will be free of this prying.  This makes it doubly important that you \emph{do not lose} these possessions or let him gain access to them.''



``He's a tinker,'' Kid Win pointed out, ``He might be able to figure out he's being watched.''



``Admittedly true, but I have assurances from Dragon that the programs and devices she has put together are sufficiently discreet.''  She clasped her hands together, ``Thank you, Wards, for your cooperation.  Your service since the start of the Endbringer event has been exemplary.  Trust me when I say I will find some way to make it up to you.''



She moved to leave, stopped, ``And Kid Win?  Good work.''



Kid Win smiled broadly.



The Wards watched in silence until the moment the elevator door closed.



``It's really freaking creepy when Piggy acts human,'' Clockblocker commented.  There were chuckles from the rest of the group.  Vista's own titter was tinged with relief.  The crack was a sign that Dennis was putting out an effort, acting more like his old self.



``Alright guys,'' Weld spoke, clapping his hands together once, generating a muted clink, ``We needed to be ready with a response in case Chariot replied, I'm sorry about interrupting your nights.  Lily, could I have a word with you before you head out again?''



Flechette nodded and followed Weld to the far corner of the room.



Vista went to get a sports drink from the kitchen in one of the alcoves.  Kid Win was sketching in a notebook.  If he was feeling inspired, it would be best to leave him alone.



She stood behind him at enough of a distance to avoid distracting him, and watched the comedy on the TV, sipping her drink.  She felt a hand on her shoulder, turned to see Weld.



Weld spoke quietly, ``You look like you could use a shower.  Go warm up, then get yourself dry and in comfortable clothes.  Clockblocker is replacing you on your patrol, you can come with me in a few hours.''



She nodded.



``Come see me when you're done.  I want to have a chat.  Nothing bad.''



She nodded again.  \emph{So Flechette said something}.



She headed into the bathrooms, detoured into the adjacent girl's bathroom with accompanying showers.  She kicked off her boots, removed her body armor, and hung the armor on one of the drying dummies.  She removed the dress and peeled off the stockings, and hung the clothes on a second dummy, where they would be subjected to a steady, gentle flow of warm air.  Her boots were placed upside down on the heating vent below the dummies, propped up against the wall.  She removed her underwear last, putting it in a basket with the rabbit Parian had made, and grabbed a towel.



It felt strange, removing her costume.  It was like she wasn't herself.  When had she started seeing herself more as Vista than as Missy Biron?  When her parents divorced, and she started taking extra shifts to get away from the oppressive atmosphere?  After one year on the team, two?



She hung the towel up and stood under the spray of hot water, rinsing off the dirt and the grime that had come with the damp, dirty water that was everywhere outside, now.  It didn't take long to soap up and rinse off, but she spent a long few minutes leaning there with her hands against one wall of the stall, letting the water run over her, not thinking about anything in particular.



She cranked the water off and walked over to the sink to look at herself in the mirror, her towel around her shoulders.



The water had removed most of it, but there was a line of dried blood flecks on her throat from where the wire had pulled against it.  She had another, similar, mark on her left arm, by her elbow.  She picked the flecks away with one fingernail, then rinsed her finger clean with a spray of water from the faucet.  Only a pink line remained.  Neither serious enough to warrant worrying about.  There was bruising on one of her knees, the thigh and around the side of her pelvis where the bone was closest to the skin, from where rubble had fallen on her, green-yellow in color.



There were older injuries too.  Small scars on her hands, tiny cuts on her legs, the bump of a dime-sized keloid scar on the top of one foot.  The one that caught her eye was on the right side of her chest, an inch and a half down from her collarbone.  An inch wide, the scar puckered inward a bit.  It had been the result of an altercation with Hookwolf as the villain escaped the scene of a grisly attack on a grocer, a year ago.  A blade on the villain's arm had punctured her armor as he'd knocked her aside.  She'd felt the pain of her skin being penetrated and she'd kept quiet about it out of a desperate need to shake the label of being the team baby.  She didn't want to be seen as the one always in need of help and protection.  It would have been embarrassing to ask for medical attention, only for it to be a scratch.



It had only been later that she'd seen how serious it was, how much it had been bleeding into the fabric of her costume, underneath her breastplate. She'd stitched it up herself, here, in the showers.  She'd done as best as she was able, worked with a kind of grim determination.  Not the most competent job, in the end.



She kind of regretted that series of decisions, now.  She was a late bloomer, looked younger than she was, but when she did eventually have the sort of cleavage she could show off, the scar would be there, plain as day.  It might even be worse, when that time came, depending on how the scar stretched as her chest grew.



Vista might have tried asking Panacea to fix it, but hadn't been able to summon up the courage.  Now, as she thought about it, she thought maybe she didn't really want to get rid of it.  A part of her took a perverse kind of pride in the fact that she had a scar, as though it was some kind of proof to herself that she was a good soldier.  It was a sort of validation of the philosophy she'd been outlining to Flechette.  Why stress about a scar on her chest when some villain could kill her before it became an issue?



A toilet flushed in one of the bathroom stalls, and Vista hurried to pull her towel from around her shoulders and wrap it around herself, hiking it up to cover the scar on her chest.



Sophia strolled over to the sink next to Vista.  She gave the younger girl a cool look, ``Don't freak out, midget.  It's not like you have anything worth hiding.''



Bristling at the midget comment and the crack about her chest, Vista just stared at herself in the mirror, ignoring the girl.



Sophia finished washing her hands, then got her toothbrush and brushed her teeth.  She took her time, while Vista stood there, clutching the towel around herself with both hands.



Finishing, Sophia put her toothbrush away, and, as she'd been doing recently, put a hand on Vista's head as she passed by.  Only this time, she mussed up the younger girl's hair, with more roughness than was necessary.  ``Carry on, kid.''



\emph{Great}, Vista thought.  \emph{Dennis might be acting more like his old self, but Sophia is too.}



She combed out her hair, sorting out the tangles that Sophia's attention had given her, dried off, and then went to her locker to get a change of clothes: A t-shirt, sweatshirt and flannel pyjama pants.  Comfortable clothes.  She pulled on slippers and went to find Weld.



Sophia was manning the console, browsing Facebook.  Kid Win was testing out the armor – four guns with the size and shape of large pears were floating around the shoulders in a loose formation.



Rather than distract Chris or have to deal with Sophia again, Vista left the headquarters and headed into the elevator.  Weld's room was in the hallways one floor up, opposite Kid Win's workshop.



The door was open, and he was there, reclining on the a heavy-duty chair of the same model as the one he had in the conference room.  He had headphones on, his feet on a granite counter where his computer sat.  She'd never been in his room.  Looking around, she saw rack upon rack of CDs, DVDs and vinyl records.  There was no bed, but he didn't really need to sleep, so that made some sense.  It was easily possible that he slept in the chair.



His head was bobbing with the music until he spotted her.  He gave her a quick nod, pulled off his headphones and turned off the speaker system.



``You wanted to talk to me?'' she asked.



``I sent Flechette on patrol with you because she's got an objective perspective on the team, and I wanted to see if her thoughts on you echoed my own.  True enough, you were only out for a short while, and she's already expressed concerns.''



``Okay.''



``Tell me straight up, are you doing okay?''



``People keep asking me that.  I'm fine.''



``Flechette said you were sounding pretty fatalistic when you were on patrol, a little while ago.  I know you were fond of Gallant, that you were pretty inconsolable when you were in the hospital, at his bedside.''



Vista looked away.



``And now you're acting like nothing fazes you, even the idea of you maybe dying in the near future.  I have to know, Missy.  Do you have a death wish?  Are you going to be putting yourself in unnecessary danger?''



``No,'' she said.  When his expression didn't change, she repeated herself, louder, ``\emph{No}.  You saw me against the Travelers.  I don't think I did anything stupid there.''



``You didn't.''



``I just want to do a good job as a member of this team.  Carry on their memory.  Act like they would want me to act.  I can work twice as hard, be twice as tough, twice as strong, if it means making up for them being gone.''



``That's a pretty crazy burden to be shouldering.''



``It's fine.''



``And it could go somewhere problematic, if you get frustrated, let it consume you, alongside this blas\'{e} attitude towards death you seem to be adopting.''



``I can deal.''



Weld sighed.  ``Maybe.  Maybe not.  You know what I think?''



Vista shrugged.



``I think you should let your teammates take some of the responsibility there.  Trust them to help carry on the legacy.''



She shook her head, ``Nobody else seems to care as much--''



Weld raised a hand, ``Stop.  Let me finish.  Remember that your teammates have their individual strengths to their personalities.  I don't know enough about Aegis or Gallant to say for sure, but I think maybe Clockblocker is stepping up to become more of a leader, in Aegis's absence.  It could be part of why there's friction between him and me, even if he doesn't fully realize it.''



``Gallant was sort of preparing to be the team leader, for when Aegis graduated,'' Vista said, her voice quiet.



Weld nodded.  ``The impression I've picked up, and forgive me if I'm off target, is that Aegis was the head of the team, the leader, strategist and manager.  Gallant, maybe, was the heart.  The guy who tied you all together, kept the interpersonal stuff running smoothly.  Would I be wrong in assuming he was the one who handled Sophia best?''



Vista shook her head.  A lump was growing in her throat.



``Okay.  With all this in mind, I have one suggestion and two orders.  My suggestion?  Stop trying to be everything they were.  Be what you're good at, a caring, sweet young woman who everyone on the team likes.  My professional opinion is that you have it in you to fill some of that void Gallant left.  Use that empathic nature of yours to help others with their own struggles.  Be the team's heart.''



Her eyes started watering.  She blinked the tears away.



``And my orders?''



``Order number one is that you go see the PRT's therapist.  If I can clear it with Director Piggot, figure out a way to make the patrol schedules work, I'm going to try to get everyone to go.  I'm honestly kind of flabbergasted that nobody higher up than me has mandated it already.''



``Okay.''  In a way, she was relieved, at that instruction.



``Order number two is to let yourself cry, damn it.  Stop holding it back.''



Just the mention of crying made her eyes water again.  Vista wiped it away once more, ``I've cried enough.''



``If your body wants to cry, then you should listen to it.  It doesn't make you any weaker if you let it happen.  You think I've never cried?  Looking like I do, facing the disappointments and frustrations I have?  Maybe it's self-serving to think so, but I think it takes a kind of strength to let yourself face your emotions like that.''



The tears were rolling down her cheeks, now.  She let her head hang, her damp hair a curtain between her and her team leader.  He stood, pulled her into a hug.  She pressed her face against his shirt.  It was soft, but the body beneath was hard, unyielding.  It was still very gentle.



When she pulled away, a few minutes later, his shirt was damp.  She sniffled, taking the offered tissue to wipe at her eyes and nose, Weld spoke, gently, ``I'm always here to talk, and the therapist will be there too.''



Vista nodded.



``If you need a break from the team, just say the word.  I'll talk to Piggot.''



She shook her head, ``No.  I want to work.  I want to help.''



``Okay.  Then we've got patrol in\ldots two hours and fifteen minutes.  Go relax, watch some TV, maybe take a nap.''



``Alright.  Don't you dare let me sleep through patrol.''



``I wouldn't.''



She made her way back to the elevator, noting the lights were on in Kid Win's workshop.  Heading back down to the base, she walked toward her cubicle-room.



``Holy crap, you've been crying \emph{again}?  I thought you were over that.''  Sophia commented from the console.  She was on her laptop, sitting just to the right of the main console.  Nobody else was present in the headquarters.  Again, the two of them were alone.  Was Sophia's nice act only for when others were around?



Vista turned, irritated.  ``I was venting a little with Weld, what's your issue?''



``I just really hate crybabies,'' Sophia turned back to the computer.



\emph{Crybaby.}  Whatever else someone could say about Sophia, there was no denying that she was very, very good at finding someone's weak points, be it during a brawl or in an argument.  Vista couldn't think of an insult that would have needled her more.



``Bitch,'' Vista muttered, moving toward her room.



She thought she spoke quietly enough that Sophia didn't hear, but the girl did, because she had a response.  ``You annoyed him, you know.''



Vista stopped in her tracks, stayed where she was, her back to Sophia.  She replied without turning around ``Weld?  You don't know--''



``Gallant.  Twelve year old following him around all the time, brimming with prepubescent lust and lovesick infatuation?  And he can feel all of her emotions?  You know how gross that would be?  How disturbing and awkward?''



Vista clenched her fists.



Sophia went on, ``Think about it, every time you got just a little turned on while you looked at him?  Every time you crushed on him?  He felt it, forced himself to smile and play nice even as you totally repulsed him, because he was that kind of guy.  You \emph{know} he was that kind of guy.''



``I \emph{loved} him,'' Vista spoke.  The first time she'd spoken the words aloud.  Why did it have to be to Sophia?  Why couldn't she have said it to Gallant, before he passed?  ``There's nothing gross about love.''



``You don't know what love is, little one,'' Sophia's condescending tone rang across the room, ``It was a first crush, a little infatuation.  Real love is what he had with Glory Girl\ldots that long-term bond that survived through a dozen really nasty fights, and brought them back together again and again.  A schoolgirl crush is easy.  Real love is \emph{hard}, something tempered and enduring.''



Vista turned to look at the older girl.



Sophia was reclining in her chair.  She smiled a little, ``I know it sucks to hear now, but it's better to hear it straight than to look back and realize how horribly stupid you sounded, five or ten years down the road.''



``I am \emph{not} going to feel stupid for how I feel now.''



Sophia shrugged, ``Kids.''  She turned her attention to Facebook.



Vista unclenched her fist.  She could tip Sophia out of her chair, bend the computer screen, carry out any number of petty revenges.  But Weld's advice stuck in her head.



``What happened to you, Sophia?''



Sophia looked over her shoulder.  ``You're still here?''



``What kind of situation led to you becoming like this?  So casually cruel, so lacking in basic human decency?''



``My advice is for your own benefit, little tyke.  I'm not the bad guy.''



``You're the only one who doesn't have any friends on the team, you keep yourself at a distance, you talk only with your friend or friends from your civilian life.  Even there, you're always in trouble.  Getting suspended, picking fights.  It's like you \emph{want} to break your probation and go to some juvenile detention facility for the next few years.''



``Not your business.''



``Out in costume, you're \emph{scary}.  You hurt people like you're hungry for it.  I just want to know \emph{why}.  Where did you come from?  What situation led to you being like this?''



``Drop the fucking subject.  You're irritating me.''



Vista sighed.  Feeling the traces of anger and the hurt from Sophia's words, she still tried to soften her parting words as she turned to go back to her room, ``If you ever do want to talk about it, I'm willing to listen.''



``I'm not about to talk about it with \emph{you}.  Fix your own shit before you start worrying about me, crybaby.''



Frustrated, disappointed in herself for failing in her first genuine effort at taking Weld's advice, trying to reach out to a team member that needed it, Vista shook her head, muttered, ``I pity you.''



The sound of a laptop crashing to the ground made Vista turn.  She saw Sophia in her shadow state, wispy, her skeleton visible beneath her skin, warped.  The girl's eyes were too reflective, her entire body seemed to bend and distort, not completely solid as she leaped towards Vista.



Sophia dropped out of her shadow state in time to push Vista flat onto her back, hard, one fist gripping the collar of the younger girl's t-shirt.  She shook her.  ``\emph{Pity}?''



Feeling strangely calm despite the pain that radiated through the back of her head, where it had struck the ground, Vista spoke, ``Weld said it takes a kind of strength to face your emotions.  Are you really that scared, Sophia, that you'd attack me instead of talk to me?''



Sophia raised a clenched fist.  Vista screwed one eye shut, anticipating the hit.  \emph{It would almost be worth it if she hit me and violate the conditions of her membership on the team, to have her gone.  But we need all the help we can get, right now}.  ``The security cameras are watching us right now.''



Sophia dropped her hand, stood, and stalked over to the far side of the room.  She gathered her costume in her arms.  ``I'm going on patrol.''



``It's not your shift,'' Vista spoke, sitting up.



``Don't fucking care.  If Weld asks, I'm doing a double shift.''



And then Sophia was gone, having used her shadow state to disappear through the elevator door.



``Okay,'' Vista spoke, pulling herself to her feet. ``Guess I'm manning the console.''





