





Shadow Stalker paused in her patrol when she arrived at the roof of the Hillside Mall, downtown.  She'd hoped to run into some looters, had had some luck earlier in the week at this spot, but it seemed that police forces were stationed at the entrances, now.  Annoyed, she walked over to the corner of the roof, so the toes of her boots were just at the brink.



She got her smartphone and dialed Emma.  The phone automatically made the wireless connection to her earbud.



``Hey, superhero,'' Emma answered.



``How's Portland?''



``Good food, good shopping, boring as hell.  I wish I could come back, hang out.''



``I wish you to come back, too,'' Shadow Stalker admitted, ``These morons are fucking pissing me off, and I'm not getting enough breaks from it.  I don't have the patience for this.''



``Which morons?  The Wards?''



``The Wards,'' Shadow Stalker confirmed.  She sat down on the ledge.  ``They're \emph{children}.''



``Yeah,'' Emma replied.  She didn't prod for more information or clarification.  Shadow Stalker had gone over this before enough times, in one variation or another.



That didn't stop her from returning to the subject, ``Sure, some of them are older.  Some have more time in the field than me.  Maybe.  But they're still children, living in their comfortable, cozy little worlds.  I dunno if you've seen what the city's like now-''



``-I saw some on the news.'' Emma interjected.



``Right.  Damaged, destroyed, \emph{fucked up}.  This is a place those kids \emph{visit}, and they're still convinced they can fix it.  I've lived with this all my life.  Waded through this shit from the beginning.  I know they're deluding themselves.  So yeah, they're immature, new to this, and I don't know how long I can fucking put up with them.''



``Two and a half more years, right?''  Emma asked, ``Then you're off probation, free to do your thing.''



``God, don't remind me.  Makes me realize I'm not even halfway through it.  I can't believe it's already been this long, constantly hearing them bitch about dating, or clothes, or allowances, and every time I hear it it's like, I want to scream in their face, \emph{fuck you, you little shit, shut the fuck up.}  I've \emph{killed people, }and then I washed the blood off my hands and went to school and acted normal the next day!''



Silence hung on the line for a few long moments.



``I remember,'' Emma spoke, a touch subdued.



Shadow Stalker chewed on her lower lip, watched a butch policewoman pull into the parking lot, then hand out coffees to the others on duty.



``If it weren't for all the crying and the complaining, I would almost be \emph{glad} Leviathan had attacked the city.  Tear away that fucking ridiculous veneer that covers everything.  Get rid of those fucking fake smiles and social niceties and daily routines that everyone hides behind.''



``Yeah?''



``Yeah.''  Shadow Stalker didn't elaborate too much further on the subject.  Leviathan had revealed the desperate, needy animal at the core of everyone in this city.  He'd made things \emph{honest}.



Most were victims, sheep huddling together for security in numbers, or rats hiding in the shadows, avoiding attention.  Others were predators, going on the offensive, taking what they needed through violence or manipulation.



She didn't care what category people fell into, so long as they didn't get in her way, like Grue had a habit of doing.  Worse yet were those who seemed intent on irritating her by being lame and depressing, like Taylor or like Vista had been this past week.



They weren't all bad.  The victim personality did have a habit of pissing her off, but she could let them be so long as the person or people in question stayed out of sight and out of mind, accepting their place without fight or fanfare.  There were some `predators', she could admit, that were even useful.  Emma came to mind, the girl went a long way towards making life out of costume tolerable, and there was Director Piggot, who had kept her out of jail thus far, because she fit into the woman's overarching agenda of PR and \emph{the illusion} of a working system.



There was a need for that kind of person in society, someone willing to step on others to get to the top, do what was necessary, so they could keep the wheels spinning.  Not all of them were so useful or tolerable, of course, but there were enough out there that she couldn't say everyone with that kind of aggressive, manipulative psychology was a blight on society.  She could respect the Piggots and Emmas of the world, if only because they served as facilitators that allowed her to do what she did best, in costume and out, respectively.



\emph{S}\emph{he} was a `predator', whether she was Shadow Stalker or Sophia.  Few would deny that, even among her own teammates.



A convoy of trucks on the road below caught her attention.  Each vehicle was painted dark, and two had the look of army vehicles, with gray-black mottled cloth or canvas covering the cargo or personnel at the rear.  They had their headlights off to avoid drawing attention.  There were two good possibilities for who they might be.  The first was that it was a shipment of supplies.  Food, water, first aid and tools, which would mean there was a small contingent of capes inside one of the trucks or in the immediate area.  The second option was that it was Coil and his troops.



She realized she was still holding the phone, and the noise of a television or music told her Emma was still on the other line.  ``Something's going on.  Going to see if it leads to anything interesting.''



``Call back when you're done, give me the recap.''



``Right.''  She hung up.



Leaping into the air, she entered her shadow state, every part of her body shifting gears in the span of a half-second.  Her lungs automatically stopped taking in air and her heart stopped beating.  She was suddenly hyperaware of changes in the atmosphere, movements of air as it passed through her body.  She had enough solidity for her body to seize the air molecules as they passed through her, and in this manner, each of her cells nourished itself.



It was strange, to feel so still.  She lacked even the most basic processes and routines that normally kept the body going, things people rarely gave a second thought to.  There was no near-silent roar of blood in her ears, no need to blink, no production of saliva in her mouth or movement of food and water in her gut.  She just \emph{existed}.



But the movement of air through her body made her feel just as alive, \emph{more} alive, in a very different way.  The material and gravel of the rooftop were still warm from the day's sunlight, even submerged beneath a thin layer of water from the rain.  This rising, heated air from this surface offered her an almost imperceptible added buoyance.  The rest of her ascent was carried out by the momentum from her leap and the fact that she was nearly weightless.  Jumping fifteen feet in the air to a rooftop one story above her was almost effortless.



She turned solid long enough to land.  Changing back brought a sudden, thunderous restarting of her heart, a shudder running through her entire body as her bloodstream jerked back into motion.  It only lasted the briefest of moments as she bent her knees and threw herself forward.  The moment her feet left the ground, she entered the shadow state once again, sailing across the rooftop.  She used one wispy foot to push herself out further as she reached the roof's edge, so she could glide just above one rooftop without even touching ground.



In this fashion, she kept pace with the trucks, which weren't moving slowly but weren't going full-bore either, likely because of the condition of the roads.



It was five minutes before trouble arrived.



It was Menja that made the first move, stampeding out of a nearby alleyway, standing at a height of twenty feet tall.  She drove her spear into the engine block of the lead truck, stepped in front of the vehicle and wrenched her weapon to tip the truck over and arrest its forward momentum.



The truck immediately behind tried to stop, but the flooded pavement made it impossible to get enough traction.  It skidded and collided into the back of the foremost truck.



Miss Militia was climbing up out of the lead truck's passenger door in an instant, hefting a grenade launcher to blast Menja three times in quick succession.  The giantess stumbled back, raised her shield – her sister's shield – to block a fourth shot.  Hookwolf, Stormtiger, and Cricket all joined the fray, followed by their foot soldiers.  On the PRT's side, the trucks emptied of PRT troops and one more cape, Assault.  They mobilized to defend, and the noise of gunfire rang through the night air.



Shadow Stalker crouched at the corner of the roof, loaded her crossbow and fired a shot at Cricket.  It passed a half-foot behind the woman.  Her second shot was on target, and Cricket dropped a few seconds later, tranquilized.  Good – The woman's radar might find Shadow Stalker if she wasn't in her shadow state, and Shadow Stalker could be far more effective if the enemy didn't see where she was attacking from.



Who else?  Menja was classified as a breaker, the spatial-warping effect that surrounded her made incoming attacks smaller even as she simultaneously made herself bigger.  The darts wouldn't even be noticeable to her.  Stormtiger could deflect projectiles by sensing and adjusting air currents.  With the right timing, so her shots came out of the shadow state as they arrived to make contact with him?  Maybe.  But he was engaged in a fist fight with Assault, and she'd be risking tagging the hero.  Hookwolf?  No point.  He was currently in the shape of a gigantic wolf made of whirring metal blades.  Even if the dart did penetrate something approximating flesh, which it wouldn't, his entire biology was so different that she doubted he would be affected.



Instead, she settled for targeting the clusters of Hookwolf's troops.  `Fenrir's Chosen'.  Each of the thugs had white face-paint extending from forehead to cheekbone to chin, in a crude approximation of a wolf's face.  She began dropping them at a steady rate, aiming for the biggest, the most aggressive and the ones who looked like they were in charge of lesser troops, the captains.  As the troops began falling, Hookwolf's forces became unsettled, hesitating to advance.  Hookwolf reared up on two legs, pointing and howling orders, likely demanding they attack.  His words were incomprehensible from the rooftop where Shadow Stalker crouched, but the tone left no mistake that he was threatening them to drive them back into the fight.



The distraction afforded Miss Militia time to prepare and fire a mortar straight into Hookwolf's chest.  As he collapsed backward, his chest cavity gaping open, her gun shimmered, split and transformed into a pair of assault rifles.  She unloaded clip after clip into the enemy ranks; rubber bullets, most likely.  The innate issues of the nonlethal ammunition were almost negligible in Miss Militia's case.  She could reform the gun in a second if a gun jammed.



Shadow Stalker watched a crowd of Hookwolf's Chosen move to flank, moving along the sidewalk, where the crashed truck blocked the view of the PRT forces.  Shadow Stalker raised her crossbow, hesitated.  She could jump down, take them down in close quarters combat.  It had been her entire reason for going out, after having to deal with the irritation of Vista.  She craved that catharsis.



She holstered her crossbow, prepared to dive into their midst, and then paused as she saw the Chosen stagger back, lashing out with their hands.  One shouted something, which was odd given how they had been trying to be stealthy only a moment ago.



\emph{What?}



Then another figure stepped out of the alleyway closest to them.  A girl, skinny, but not in the attractive way you saw in magazines.  Spindly.  Was that the right word?  The girl was hard to make out in the gloom – there were no lights on the street, and the only light was what filtered from the moon and through the rain clouds.  The girl glanced left, around the back of the truck, then glanced right, where she might have seen Shadow Stalker if she looked up just a little.  The lenses of her mask caught the moonlight, flashing a pale yellow.



\emph{Skitter}.



A feral smile spread across Shadow Stalker's face, beneath her mask.



Shadow Stalker resisted the urge to jump down, watched as the shadow of the bug girl's swarm moved over the Chosen, almost obscuring them from view.  The bug girl drew her combat stick, whipped it out to full length, and dispatched the Chosen one by one.  Shadow Stalker couldn't see the hits, between the darkness and the obscuring mass of the swarm, but she saw the splashes and movements of the Chosen as they fell to the ground, clutching their faces, knees, and hands.



Some of the bugs flowed out to pass over the PRT forces and the Chosen.  The thugs started recoiling and slapping at themselves, but Shadow Stalker couldn't see much reaction from the PRT forces.  They were made of sterner stuff, in a way, and their uniforms covered them thoroughly enough that the bugs wouldn't do nearly as much damage, if they were even attacking.



Skitter emerged from the center mass of the swarm, carrying a bag of supplies from the truck.  It was green canvas, large, not dissimilar to a gym bag.  Pulling the strap over one shoulder, she briskly retreated back into the alley, the bugs trailing after her like the tail of a slow moving comet, or the steady trail of smoke from a candle.



``Hungry, are you?'' Shadow Stalker murmured to herself.  She shifted into her shadow state, moved along the rooftop to follow the girl.  Shadow Stalker was almost entirely silent in this state, virtually impossible to see, especially in this light, unless someone was actively looking for her.  She was a gray shadow against a background of black and shades of gray.



\emph{You saw my face.}  Shadow Stalker thought, \emph{Records say you've got no team, now.  Operating alone between the old Boardwalk and the east end of Downtown.}



She leaped to the next rooftop, and the movement carried her a little ahead of her target, helped by the fact that the bug girl was moving a little slower with her burden.  Shadow Stalker paused and reached up beneath her cloak and between her shoulder blades.  She withdrew a cartridge for her crossbow, each bolt loaded in at a slight angle, so the aluminum `feathers' at the tail of each bolt stuck out.  She popped out one bolt to examine it, then turned it around so the barbed, razor sharp arrowhead caught the moonlight.  As Skitter passed beneath her, she turned the bolt's point so her perspective made it appear to be at the girl's throat.



\emph{Operating solo means there's nobody to miss you}.



She entered her shadow state and moved further along the rooftop, only to feel a group of flying insects pass through her body.  A fraction of a second later, Skitter was running, abandoning the bag, disappearing around a corner, not even turning to look Shadow Stalker's way.



``You want to run?  I don't mind a bit of a chase,'' Shadow Stalker smiled behind her mask, loading the cartridge into her right-hand crossbow.  She leaped after the girl, gliding down to street level, rebounding off a wall to turn the corner and give pursuit.



Skitter had turned around, was waiting as she rounded the corner.  The bug girl sent a mass of insects out to attack.



The bugs passed through Shadow Stalker's body, slowing her momentum.  She suspected that if there were enough of them, they could even carry her aloft, push her back.  But there weren't – the swarm wasn't quite big enough.  As the stream of insects passed through her, reoriented in preparation to flow through her again, she pounced.



The residual bugs threw her off, slowing down her power.  Her body had to push them out of the space it wanted to occupy, delayed the change back to her normal self by a half-second.  Her hand passed through Skitter's throat, but she caught her balance, drew her rearmost foot up and back in a half-spin.  Her heel collided with Skitter's mask.



Skitter went down, and Shadow Stalker turned her crossbow on her fallen opponent.  She was about to fire when the combat stick lashed out.  She lifted the crossbow up just in time –  had she been a second slower, the stick might have broken her weapon.  Acutely aware of the bugs clustering on her, she dropped into her shadow state before they could crawl beneath her mask.



The stick passed through her head, once.  She resisted the urge to snap back to her normal form and retaliate.  The girl was powerless here.  Shadow Stalker could afford to hound her, drive her to the brink of desperation, wear her down.



The bug girl switched to a one-handed grip on her baton, flying insects clustering around her to mask her movements as she backed away a step.  She used her free hand to push the wet hair out of her face.  Then she adjusted her costume, reaching to tug her shoulderpad forward a bit, then reached behind her back to do much the same with the armor there.



``You \emph{really} want to fight me?'' Shadow Stalker asked her opponent, a note of incredulity in her voice.  She raised her right crossbow.  The one with the lethal ammunition.



Skitter didn't reply.



Whatever else Shadow Stalker might think of the bug girl, how the girl was creepy, a freak, she had to admit Skitter had demonstrated enough viciousness to date that she could almost respect the girl as a fellow predator.  An idiot, for wanting to fight her, but kindred, in a fashion.  ``Alright, fine.''



Skitter gripped her weapon two-handed again.  The grip was strange.  Something in her left hand?



Shadow Stalker realized what it was.  She simultaneously moved back, gripped her cloak with her left hand and shifted to her solid state to raise the fabric as a barrier.  The pepper spray spattered her cloak.



When she was sure the spray had dissipated, she threw her cloak back over one shoulder and shifted to her shadow state to escape the bugs that were crawling on her, taking advantage of her solidity.   She lunged after Skitter, who was running, already turning a corner at the other side of the alley.



\emph{Good runner, but I'm faster}.



Shadow Stalker didn't need to slosh through the water, but she knew she would be faster than the other girl even if she did.  It wasn't just her shadow state eliminating wind resistance, or the lightness of her body.  She was a trained runner.



She bounded from one wall of the alley to the one opposite, staying above the water, pursuing her target.



Skitter was going up the steps of a fire escape.  Shadow Stalker aimed and fired a bolt – the girl ducked, and the shot clipped a railing instead.



\emph{Good reflexes.  }Shadow Stalker brushed away at the bugs massing around her.  \emph{Or do your bugs help you watch what I'm doing?}\emph{Disturbing little freak}.



Apparently deciding the fire escape wasn't a great option, Skitter climbed over the railing and leaped a half-story down to the pavement, putting a chain link fence and some accumulated trash bags between herself and Shadow Stalker.



\emph{Moron}.  \emph{I can walk through that fence}.  She loaded her crossbow, aimed, and fired through the fence at the girl.



A flash and spray of sparks erupted as the shot made contact with the fence.  Skitter stumbled as the bolt hit her, but Shadow Stalker couldn't see if it had done any damage.



No, what concerned her was the flash.  She ignored the fact that Skitter was disappearing, entered her solid state and touched the side of her mask.



Lenses snapped into place, showing a blurry image of the alley in shades of dark green and black.  The chain link fence, however, was lit up in a very light gray.  Similarly glowing, a wire was stapled to the brick of the building next to the fence, leading to a large, pale blob inside the building.  A generator.



The fence was electrified.



Shadow Stalker snarled at what had almost been a grave mistake, entered her shadow state and leaped up and over the fence, being careful not to touch it.



One of the reasons she couldn't move through walls at will, beyond the huge break in her forward momentum and the excruciating pain that came with stalling in the midst of a wall, was \emph{wiring}.  She remained just as vulnerable, maybe even \emph{more} vulnerable, to electrocution.  The people in the PRT labs couldn't tell her if she could be killed by electrocution – traditional organs were barely present in her shadow state – but it was one of those things that couldn't be properly tested without risking killing the subject.



End result?  She had to be careful where she went, had received tinker-made lenses to help her spot such threats.



Skitter had known the fence was electrified, judging by the route she'd taken through the fire escape.  The area here didn't have any power, so the question was whether it something this area's inhabitants had set up to protect themselves\ldots or was it a trap Skitter had put in place well in advance?  No.  More likely the girl had studied this area before carrying out any crimes.



Still, it troubled her that the girl had thought to use the fence like she had.  She \emph{really }didn't like the idea that the villain had not only seen her face, but that she might have figured out one of her weaknesses.  Two, if she counted the pepper spray.  Being permeable was a problem when she absorbed gases, vapors and aerosols directly into her body.  It wouldn't affect her if she was in her shadow state, and it would eventually filter out, but if she were forced to change back, she'd suffer as badly as anyone, if not worse.



Shadow Stalker caught up to the girl yet again, saw Skitter running with her swarm clustered tightly around her.  Was the girl wanting to make herself a harder target?



Hardly mattered – Shadow Stalker loaded and fired another bolt.



At the same instant the bolt fired, the swarm parted in two.  Two swarm-wreathed figures covered in bugs, each turning at a right angle to round a corner.  The bolt sailed between them.  One was a decoy, just a swarm in a vaguely human shape.



She checked the sides of the alley and the recessed doors.  Could they both be decoys?  She couldn't see any obvious hiding spots that Skitter could have used at a moment's notice.



Shadow Stalker closed the distance, placing herself at the intersection between the two bug-shrouded figures.  Holding each crossbow out in an opposite direction, she fired at both targets at once, snapping her attention from one to the next in an attempt to see which reacted to the hit.



One slowed, began to topple.  She lunged after, in pursuit, loaded her crossbow and fired two more shots into the center mass of Skitter's body while airborne, then kicked downward with both feet as she landed, to shove the girl into the ground.



Her body weight dissolved the blurry silhouette into a mess of bugs.  A trick.



Snarling, Shadow Stalker wheeled around, ran in the direction the other half of the swarm had gone  Had the girl's armor taken the bolt?  Had the crossbow shot missed?



More bugs were flowing from the area to join the swarm, bolstering its number enough for it to split again.  She wasn't close enough to be sure of a hit, and she didn't want to waste her good arrows, so she delayed, leaped forward to close the gap.



The swarm split once more, making for four vaguely human figures in total, each cloaked in a cloud of flying insects.



Shadow Stalker snarled a curse word.



One figure turned on the spot, moved as if to slide past Shadow Stalker.  She lashed out, striking it in the throat, failed to hit anything solid.



She loaded her crossbows, fired at the figure on the far left and the far right of the trio.  No reaction.  She dove after the remaining one.



She made contact, drove the bug girl's face down into the water.  She shifted into her shadow state, straddling Skitter.   The girl turned over of her own volition – easy enough, as Shadow Stalker was barely solid, but when Skitter tried to stand, Shadow Stalker resumed her normal form for a second – just long enough to force the girl back down.



Picking one of her non-tranquilizer bolts from the cartridge, she held the point of the ammunition to Skitter's throat like a knife, ``Game over, you little freak.''



Skitter cocked her head a little, as if analyzing Shadow Stalker from a different perspective.



``What are you looking at?'' Shadow Stalker spat the word, ``Nothing to say?  No last words?  No begging?  No fucking apologies?''



Skitter went limp, letting her head rest against the ground, the water lapping over most of her mask.  Dark curls fanned out in the water around her, swaying as the water rippled.



``Guess I don't need to worry about the villain who saw my face, now.''  Shadow Stalker went solid and drew the razor-sharp tip of her bolt across Skitter's throat.



The fabric didn't cut.



Skitter struggled to get free, but Shadow Stalker's body weight was too much for her to slide free.  She gripped the girl's wrists with her hands, pinned them to the ground.



``Irritating,'' she spat the word.  She could always go into her shadow state, stick the arrow inside the girl and then return to normal.  The problem with going that route was that it left a very characteristic imprint in the victim.  She would need a way of covering up the evidence.  Something she could hit Skitter with afterward that would make the wound too messy to analyze for evidence.



While she craned her head to one side to the next to search for something useful, her surroundings were plunged into darkness.



It took her only a moment to realize what that meant.  She climbed off Skitter, moved to run.  The darkness was oppressive, sluggish in moving through her, unlike ordinary air.  She was slower, wasn't taking in enough oxygen.  Against her will, her power instinctively adjusted, shifted her into a middle ground between her regular self and her shadow state.  It left her slower, heavier.



\emph{She baited me}.



A massive shape tore through her, dissipated her entire body.  She pulled back together, but it was hard, painful and uncomfortable on an unspecific, fundamental level.  It left her breathing hard, feeling like she'd just put her body through five hours of the hardest exercise of her life.  \emph{Enervating}, \emph{was that the right word}?  Bugs were gathering inside and around her body, making it a little harder and a little more time-consuming to pull together.



Then, before she had succeeded in pulling herself all the way together, it happened again, another large form striking from another direction, passing through her lower body.



She sagged.  Gasped out in pain as another shape passed through her head and shoulders.  The darkness absorbed her cry so it barely reached her own ears.



It was only seconds later that the darkness dissipated.  She was on her hands and knees, barely had the strength to move, let alone fight.  She tried to raise her right crossbow, but her hand seized up, no longer under her own control as it bent to a pain like a bad Charlie horse.  Her fingers curled back, and the crossbow tumbled from her fingers.  She still had one in her left hand, but she was using the heel of that hand to prop herself up.



Her opponents were revealed as the shadows passed, arranged in a rough ring around her.  Hellhound and her dogs took up half the clearing, in front of Shadow Stalker.  She held a metal ring in each hand, with two chains extending out from each ring.   The chains, in turn, were connected to harnesses around the heads and snouts of the `dogs', each animal only a little smaller than a refrigerator.  They were monstrous, with scaly, horned exteriors and exposed muscle.  Not as big or ugly as they could get, Shadow Stalker knew.  The smallest one was barking incessantly.  Three of the four were pulling on the chains, hungry to get at Shadow Stalker, clearly intent on tearing her apart.  Hellhound's sharp pulls on the chains contracted the bindings around their snouts, which made them stop before they could get too close.



Grue stood to her left, arms folded, almost indistinguishable from the darkness behind him.  After her first humiliating loss to him, she'd made it a mission to drive him out of this city.  He'd stubbornly refused.  A girl Shadow Stalker didn't recognize stood just behind him, wearing a black scarf and a pale gray mask with pointed horns arching over the top of her head.  The eyes of the mask had lenses that were black from corner to corner, stylized to look fierce, more animal than human.



Rounding out the group were Tattletale, Regent and Skitter.  Tattletale smiled, her hands clasped behind her back, while Regent twirled his scepter in his fingers.  Skitter stood between the two of them.  The bug girl bent, then crouched until she was almost at eye level with Shadow Stalker.



A laugh escaped Shadow Stalker's lips, building until she couldn't balance her upper body on her weakened arm.  She bent so one shoulder hit the ground, rolled onto her back, arms at her sides.  She looked up at Skitter, ``All that drama, all that fucking nonsense about allegiances, betraying your team, was it a trick, some joke?''



Skitter shook her head slowly.



Shadow Stalker tried to rise, but the growling of one of the dogs intensified.  It was the only one that wasn't pulling on its chain – the largest and most monstrous of the four, with one empty eye socket.  Between the threat of the dog and the lack of strength in the arm that Regent wasn't fucking up, Shadow Stalker gave up and let herself slump down.



``Well,'' she spoke, her tone sarcastic, ``How wonderfully fucking nice for you, that you guys patched things up.  You even have a new member, congratulations.  I guess everything's back to normal for you freaks.''



``No\ldots''  Skitter spoke, and the bugs around her chirped, buzzed and droned to match the pitch and tone of her words.  The villain hadn't done that when the Undersiders attacked the fundraiser, she remembered.   Her voice was quiet, which only made it more eerie.  The girl held out her hand, and Regent passed his scepter to her.



``\ldots{}Things are different now,'' Skitter finished.



Skitter drove the scepter into Shadow Stalker's body.  It was everything Shadow Stalker could do to stay solid as she felt the tines of the crowned stick biting through the fabric of her costume and into her stomach.  She resisted the instincts that two and a half years of exercising her powers had lent her, because she knew what came next.  \emph{It'll be worse if I'm in my shadow state}, \emph{maybe lethal}.



Being tased didn't hurt as much as she'd expected.  It was like being doused in ice water, her entire body seizing, straining, and refusing to cooperate, the pain almost secondary.  What hurt most was the way she involuntarily clenched of her jaw.  The strength with which her teeth pressed together made her worry she might crack a tooth.



It only lasted a moment, but her body wasn't any more cooperative after the current subsided.  She lay there, huffing small breaths, every limb unresponsive.  A deep, furious rage grew inside her chest, but she was impotent to do anything to release it.



A pair of hands seized her, sat her up.  Her arm dangled limp to her side.



Grue spoke from behind her.  ``Skitter, lift her legs.  Regent, support her midsection.  Imp?  Give me a hand with her upper body, take the other shoulder.  We lift on three, alright?''



``Right,'' someone said.



``One, two, three!''





