





The place was nondescript.  A hole in the wall in the midst of a long street of hole in the wall businesses.  Everything was run down.  For every given store or restaurant you passed, you could only guess if the place was still open or not.



The pub had a sign on it reading `Somer's Rock'.  There were iron bars on the windows and the curtains were drawn, but it would have been more unusual if that wasn't the case.  It was that kind of area.  The paint on the outside was peeling, and the rust from the bars had bled onto the gray-white paint below the windows.



As we stepped inside, it became clear that Somer's Rock was one book that should be judged by its cover.  It was dim, dingy and depressing.  The wood floor was stained the same dark gray as the counter of the bar, the curtains and tablecloths were dark green, and the only real color or brightness, if you could call it that, was the yellow light cast by ancient, burnt lightbulbs.



There were three people in Somer's Rock when we arrived.  One was a sullen looking twenty-something girl with brown hair and a slightly wrinkled server's uniform, who glanced at us as we came in, but made no attempt to welcome us.  There were two identical twins behind the bar in the far corner, probably her older brothers, busying themselves with washing glasses and studiously ignoring us.  One of them was wearing a dress shirt and apron, looking the part of a bartender, while the other had a black t-shirt under a Hawaiian shirt.  Besides the contrast in fashion, they were identical in height, haircut, features and expression.



A group of tables had been pulled together with chairs arranged around them, but we walked past them to a corner booth.  Tattletale, Bitch, Grue, Regent and I all arranged ourselves on the worn cushioned benches.  I was calling them that in my head, really, because they \emph{weren't} Lisa, Brian, Rachel and Alec.  We were all in costume.



As we settled in, the girl with the dour expression approached us, setting her notepad down on the table and then stared at me, the look in her eyes almost challenging.  She didn't say a word.



``Coke?'' I ventured, feeling uncomfortable under the look.



``No, Skitter,'' Tattletale nudged me, ``She's deaf.  If you want something, write it on the pad.''  To demonstrate, she reached across the table, took the pad and wrote `tea, black'.  I took her cue and wrote down my order, then passed the note across the table to the boys and Bitch.  The girl gave me an ugly look as she walked away with our orders.



It had been a week since the incident with Bakuda.  Lisa and Brian had stopped by several times as I spent my days in bed, giving me updates on the situation as it unfolded.  At one point they had even brought Alec and Bitch, and I'd been \emph{very} relieved my dad hadn't been home at the time.  Alec and Bitch weren't the polite houseguests that Lisa and Brian were, and I suspected their presence and personalities would have raised more questions with my dad than they put to rest.



Apparently someone at the PHQ had named my costumed self `Skitter'.  Lung had overheard something about it, and it had now spread through the city in the aftermath of his escape, which implied he was probably looking for me.  As a newspaper article raised our possible involvement in the bombings that had taken place, as adversaries of Bakuda, my new name had come up yet again, so it looked like it was maybe catching on.  I didn't love it, but I didn't love \emph{any }of the names I'd come up with, so I could cope.



It seemed that we had arrived a few minutes early, because the rest of the guests arrived within seconds of each other, as the server brought us our drinks.



Kaiser came through the door with a girl on each arm, blondes with measurements like Playboy models.  Kaiser wore armor head to toe, elaborately worked and topped with a crown of blades.  The leader of Empire Eighty Eight.  The twins went by the names Fenja and Menja, and were decked out in Valkyrie-style armor featuring countless little steel wings, along with closed-face helms.  Had to admit, Kaiser liked his heavy hitters.  These two could grow to be three stories tall, and they were a hundred times more durable when they were.



Purity entered a few steps behind him with several others following her.  She was dressed in a white costume without any markings or symbols on it, but the fabric glowed softly.  Her white hair and eyes glowed too, but it was more like they were made of heated magnesium than anything else.  I couldn't look in her direction without getting spots in my eyes, and my mask had tinted lenses \emph{designed} to reduce glare.



The people that had come in with Purity were other members of Empire Eighty Eight.  Krieg, Night, Fog and Hookwolf.   It was interesting to see, because as far as I'd known, while every one of them had been a member of Empire Eighty Eight at some point in time, Purity had gone solo, while Night and Fog had splintered off to form their own duo in Boston not long after.  All reunited, apparently.



That wasn't even Kaiser's entire team.  Aside from the rare exception like Lung reaching out to Bakuda when she'd been at Cornell, it seemed that most groups recruited new members from within their own city.  Kaiser was different.  He was one of the better known American villains with a white supremacist agenda, and people sharing his ideals were either recruited from other states or they came to him.  Most didn't stay with him for too long, for whatever reason, but it still made him the Brockton Bay resident with the most raw parahuman muscle at his beck and call.



Kaiser sat at one end of the table in the center of the room, his people finding seats and chairs at the tables behind him.  Purity didn't relax or order drinks, though.  She sat in a chair a few feet behind Kaiser, folded her arms and crossed one ankle over the other, settling in to watch the proceedings.  From my research online and digging through old newspaper articles,I knew Purity could create light and charge it with kinetic energy.  She was like a human flashlight, if the light from the flashlight could punch through brick walls and tear city buses in half.  As far as raw firepower went, she was up near the top of the list, a flying artillery turret.



Coil entered after Empire Eighty Eight, all the more conspicuous because he was alone.  No backup, no show of force.  He was taller than Grue, but he was thin to the point of being skeletal.  His skintight costume covered him head to toe, lacking even eyeholes or openings for his nose and mouth, and the way it clung to his skin let you see his individual ribs and joints.  The costume was black, and the only design on it was a white snake, with its head starting at Coil's forehead, the tail extending down the back of his head, looping and winding over his entire body before finally ending at one of his ankles.  He sat at the end of the table opposite Kaiser.



``What's his deal?'' I whispered to Tattletale.



``Coil?  Can't say as far as his powers go, but he's one of the more powerful players in town.  Considers himself a chessmaster.  You know, like a master strategist, tactician.   Controls more than half of downtown with squads of top notch personnel in the highest end gear.  Ex-military from around the world.  If he even has powers, he's the only one in his organization who does.''



I nodded.  Almost the opposite of Kaiser in that department.  I might have asked more, but others were streaming into the room.



Faultline.  I knew of her from my research.  She was twenty-something, and her straight black hair was in a long bristling ponytail.  Her costume was weird, approximating something like a blend of riot gear, a martial arts uniform and a dress.  Four people entered the room with her, and the two guys in the group were instantly the weirdest people in the room.  I knew them by name too.  Newter wasn't wearing a shirt, shoes or gloves, which made it all the more apparent that his skin was neon orange from head to toe.  He had light blue eyes, dark red hair that looked wet and a five foot long prehensile tail.  Gregor the Snail was morbidly obese, average height, with no hair on his entire body.  His skin was milky white and slightly translucent, so you could see shadows beneath it where his organs were.  Like someone else might have bad acne, he had bits of shell or scales crusting his skin.  They looked almost like barnacles, but there was a spiral shape to them.



You wouldn't have thought they were close by their body language, silence and the sheer difference in appearance, but both had matching tattoos.  Newter's was just above his heart, while Gregor's was on his upper arm.  It looked like the greek `Omega' symbol, but upside down.  Maybe a stylized `u'.



The other two girls in Faultline's group were very normal by contrast;  Labyrinth wore a dark green robe and mask with lines all over them.  Spitfire wore in a red and black costume with a gasmask.



I was surprised when Faultline deliberately walked by our table on her way to her seat, taking the long way around.  As she passed us, she looked over Tattletale and me and sneered a little before taking the chair to Kaiser's right.



``I'm going to go before all the seats get taken, if that's cool?'' Grue spoke, and the rest of us nodded.  Grue sat between Faultline and Coil.



``What was that with Faultline and you?'' I murmured to Tattletale, ``History?''



``Nothing important,'' she replied.



Regent leaned forward.  ``She and Tattletale have been feuding a little.  Faultline upped the ante when she poached Spitfire from us when we were in the middle of trying to recruit her.  Can't say why Faultline doesn't like Tattle, but I know Tattletale hates it when people act like they're smarter than her, and Faultline \emph{is }smarter than her.  Ow.  Fuck, that hurt.''



Tattletale had kicked him under the table.



``They're mercenaries right?'' I asked.



Tattletale nodded, ``Faultline's crew does anything short of murder.  You can say her personality sucks, you can say her \emph{powers} suck, but I'll admit she's very good at finding hidden strengths in the people that work for her.  See those two guys?  When it came to powers, they got a bad roll of the dice.  Became freaks that couldn't hope to pass in normal society, wound up homeless or living in the sewers.  There's a story behind it, but they became a team, she made them \emph{effective, }and they've only messed up one or two jobs so far.''



``Gotcha,'' I said, ``Impressive.''



``Keep in mind, though, we haven't screwed up \emph{any}.  We're 100%.''



``They've done something like three times as many jobs as us,'' Regent pointed out.



``But we haven't failed any jobs, is the important thing,'' Tattletale stressed.



Another group arrived, and it was like you could see a wave of distaste wash over the faces in the room.  I had seen references on the web and news articles about these guys, but they weren't the sort you took pictures of.  Skidmark, Moist, Squealer.  Two guys and a girl, the lot of them proving that capes weren't necessarily attractive, successful or immune to the influences of substance abuse.  Hardcore addicts and dealers who happened to have superpowers.



Skidmark wore a mask that covered the top half of his face.  The lower half was dark skinned, with badly chapped lips and teeth that looked more like shelled pistachio nuts than anything else.  He stepped up to the table and reached for a chair.  Before he could move it, though, Kaiser kicked the chair out of reach, sending it toppling onto its side, sliding across the floor.



``The fuck?'' Skidmark snarled.



``You can sit in a booth,'' Kaiser spoke.  Even though his voice was completely calm, like he was talking to a stranger about the weather, it felt threatening.



``This is because I'm black, hunh?  That's what you're all about, yeah?''



Still calm, Kaiser replied, ``You can sit in a booth because you and your team are pathetic, deranged losers that aren't worth talking to.  The people at this table?  I don't like them, but I'll listen to them.  That isn't the case with you.''



``Fuck you.  What about this guy?'' Skidmark pointed at Grue, ``I don't even know his name, and he's sitting.''



Faultline answered him, ``His team hit the Brockton Bay Central Bank a week ago.  They've gone up against Lung several times in the past and they're still here, which is better than most.  Not even counting the events of a week ago, he knows about the ABB and he can share that information with the rest of us.''  She gave Grue a look that made it clear that he didn't have a choice if he wanted to sit at the table.  He dipped his head in the smallest of nods in response.  We'd discussed things beforehand and agreed on what details we'd share.



``What have \emph{you} done that's worth a seat at this table?'' she asked Skidmark.



``We hold territory-''



``You hold nothing,'' Grue answered, raising his voice, his powers warping it, ``You're cowards that hold onto the areas nobody else cares about, making drugs and selling them to children.''



``We sell to \emph{everyone}, not just-''



``Find a booth,'' Grue's echoing voice interrupted him.  Skidmark gave him a look, then looked at the others sitting around the table.  All still, every set of eyes he could see behind the masks was staring him down.



``Assholes.  Puckered, juicy assholes, all of you,'' Skidmark snarled, stomping off to the booth where his teammates already sat.



The serving girl picked up the fallen chair and restored it to its position at the table, not meeting anyone's eyes as she walked up to the table where Kaiser's people sat, put down her notepad and waited for everyone to write down their orders.  It struck me just \emph{why} the pub had a deaf waitress.



``I'll be taking a chair, I think,'' someone spoke from the door.  Most heads turned to check out a male figure in a black costume with a red mask and tophat.  It gave me sort of a Baron Samedi vibe.  His teammates followed him into the room, all in matching costumes of red and black, differing only in design.  A girl with a sun motif, a guy with bulky armor and a square mask, and a creature so large it had to crawl on its hands and knees to get through the door.  It was hard to describe, approximating something like a four armed hairless gorilla, with a vest, mask and leggings in the red and black style its team was wearing, six-inch claws tipping each of its fingers and toes.



``The Travelers, yes?'' Coil spoke, his voice smooth, ``You're not local.''



``You could call us nomadic.  What was happening here was too interesting to pass up, so I decided we'd stop by for a visit.'' The guy with the top hat pulled off the first really formal bow I'd seen in my life. ``I go by Trickster.''



``You know the rules, here?'' Grue asked Trickster.



``We've been to similar places.  I can guess.  No fighting, no powers, no trying to bait others into causing trouble, or everyone else in the room puts aside all other grievances to put you down.''



``Close enough.  It's important to have neutral ground to meet, have civilized discussion.''



``I won't argue that.  Please, continue as if I wasn't here.''



When Trickster took a chair and put his feet up on the table, nobody complained, though Skidmark looked like he wanted to kill someone.  The rest of the Travelers settled in a booth not far from us.  The gorilla thing sat on the floor and it was still large enough to be at eye level with its teammates.



Coil dipped his head in a nod and steepled his fingers.  When he spoke, his voice was smooth, ``That should be everyone.  Seems Lung won't be coming, though I doubt any of us are surprised, given the subject of tonight's discussion.''



``The ABB,'' Kaiser replied.



``Thirty five individuals confirmed dead and over a hundred hospitalized in this past week.  Armed presence on the streets.  Ongoing exchanges of gunfire between ABB members and the combined forces of the police and military.  They have raided our businesses and bombed places where they think we might operating.  They have seized our territories, and there's no indication they intend to stop anytime soon,'' Coil clarified the situation for all present.



``It \emph{is} inconvenient,'' Kaiser spoke.



``They're being reckless,'' Faultline said.  She made it sound like that was a crime on par with killing kittens.



Coil nodded, ``Which is the real concern.  The ABB can't sustain this.  Something will give, they will self destruct sooner or later, and they will likely cease to be an issue.  Had things played out differently, we could look at this as a good thing.  Our problem is that the actions of the ABB are drawing attention to our fair city.  Homeland security and military forces are establishing a temporary presence to assist in maintaining order.  Heroes are flocking to the city to support the Protectorate in regaining control of matters.  It is making business difficult.''



``Bakuda is at the center of this,'' Grue joined the dialogue, ``Lung may be the leader, but everything hinges on the girl.  She `recruited' by orchestrating raids of people's homes while they slept, subduing them, and implanting bombs in their heads.  She then used those bombs to coerce her victims into kidnapping more.  No less than three hundred in total, now.  Every single one of her soldiers knows that if they don't obey, Bakuda can detonate the bombs.  All of them are willing to put their lives on the line, because the alternatives are either certain death or watching their loved ones die for their failure.  Taking her down is our ultimate goal, but she's rigged her bombs to go off the second her heart stops, so it's a little more complicated than a simple assassination.''



He reached into the darkness that shrouded his chest and withdrew a package.  ``She videotaped the ambush she pulled on my group a week ago and left it behind when she ran.  I've made copies.  Maybe you'll find it useful for getting a better understanding of her.''



Grue handed a burned CD to everyone at the table.



This was \emph{our} show of strength.  The video showed everything from the point Bakuda had liquefied Park Jihoo to the second bomb she had set off in her ranks.  As the second bomb had gone off in the midst of Bakuda's group, the camera had dropped briefly, recorded the sounds of guns going off and everything being darkened by Grue's power, but it didn't show us running.  It didn't reveal our weaknesses, how lucky we'd been to get away, or how bad our circumstances had really been.  It \emph{did} let everyone know what we'd been up against, let them know that we'd come out fine and had been able to attend this meeting.  That would do as much for our reputation as anything else.



I wasn't 100\% recovered from my concussion, and Alec was complaining of twinges in his arm, still, but Brian had stressed how important it was that we attend, give the illusion our team was intact, untouched. Seeing the other groups with their subtle posturing, I knew he'd been right.



``So,'' Coil let the word hang in the air as he cracked each of the knuckles on his right hand individually, ``We're in agreement?  The ABB cannot be allowed to continue operating.''



There were nods and murmurs of agreement from around the table, some from the various villains gathered around the room.



``Then I suggest we establish a truce.  Not just everyone here, but between ourselves and the law.  I would contact authorities and let them know that until this matter is cleared up, our groups will restrict our illegal activity to only what is absolutely essential to our business, and we will enforce the same for those doing business in our territories.  That would let police forces and military focus entirely on the ABB.  There would be no violence, infighting between our groups, grabs for territory, thefts or insults.  We band together with those we can tolerate for guaranteed victory, and we ignore those we cannot cooperate with.''



``Just saying my group won't be getting directly involved in this without a reason,'' Faultline spoke, ``We won't be going after the ABB unless they get in my way or someone pays my rates.  It's the only workable policy when you're a cape for hire.  And just so we're clear, if it's the ABB paying, my team's going to be on the other side of things.''



``Unfortunate, but you and I can talk after this meeting is done.  I'd prefer to keep matters simple,'' Coil said, ``You're okay with the other terms?''



``Keeping on the down-low, not kicking up a fuss with other groups?  That's status quo with my group anyways.''



``Good.  Kaiser?''



``I think that is acceptable,'' Kaiser agreed.



``I was talking to my group about doing something not too different from what Coil just proposed,'' Grue spoke, ``Yeah, we're cool with it.''



``Sure,'' Trickster said, ``Not a problem.  We're in.''



Hands were shaken around the table.



``Funny,'' Tattletale murmured.



I turned away from the scene to look at her, ``What?''



``Aside from Grue and maybe Faultline, everyone's already plotting how they can use this situation to their advantage, or fuck over the others.''



I turned back to the scene, the villains sitting around the table.  It dawned on me just how much sheer destructive potential was gathered in the room.



This could get complicated.





