





Coil addressed the room, ``Then that's our major piece of business concluded tonight.  Anything else before we go our separate ways?  Offers, announcements, grievances?''



``I've got a complaint,'' a man at the side of the room spoke.  Heads turned to Kaiser's group.  Hookwolf.



He wore a mask that was little more than a piece of sheet metal cut and shaped to resemble a wolf's features, attached to his head with straps of black leather.  He had a chain threaded through the belt loops of his jeans, sporting a heavy metal belt buckle.  The buckle featured a wolf superimposed on a swastika – the same image he had tattooed on one of his biceps.  The opposite arm simply had `E88' on it.  Outside of the mask and the belt buckle, you couldn't really say he had a costume.  He was shirtless, shoeless, and hairy.  His blond hair was long and greasy, and he had thick hair on his chest, stomach and arms.  Harpoon-like spears and metal that curled like fishhooks radiated out from his shoulders, elbows and knees, all bristling with barbs or wickedly serrated edges.



Nobody, to date, had ever escaped the Birdcage, the name that had been coined for the supervillain prison in British Columbia.  Hookwolf, though, had escaped on no less than two occasions while being transported there.  He was a killer, and thought nothing of murdering people if they didn't fit the Aryan ideal.



He turned to look at our table, very pale blue eyes visible through the slits in his metal mask, ``My complaint's with her.''



``What's the issue?'' Grue's voice was calm, but it looked like he was generating a bit more darkness around him than he had been, making himself look a fraction bigger.  I wondered if he knew he was doing it.



``The crazy one, Hellhound, she-''



``Bitch,'' Bitch interrupted him, ``Only the panty-ass heroes call me Hellhound.  It's Bitch.''



``Don't fucking care,'' Hookwolf growled, ``You attacked my business.  Set your fucking dog on my \emph{customers}.  Lucky I wasn't there, whore.''



Grue gave Bitch a long look, then he spoke to Hookwolf, ``That's the kind of risk you run, doing business in Brockton Bay.  Capes can and will get in your way, hero or villain.''



Hookwolf glared at him, ``It's a matter of respect.  You want to fuck with my business, and we're not at war?  You let me know if you've got an issue, first.  Let me decide if I want to move shop.''



``You mean give you a warning I'm coming,'' Bitch spat the words, ``That's the dumbest fucking thing I ever heard.  Just so you know, moving to a different neighborhood won't be good enough.  You open up another dogfighting ring, I'll be visiting that one too.''



Oh, that's what she'd done.  I glanced at Tattletale, then at Grue.  I was getting the impression neither of them had known.



Kaiser spoke, ``Is that a declaration of war, Undersiders?  We just agreed to a truce, if you recall.''  He was utterly calm, a stark contrast to Hookwolf.  Hookwolf was brimming with barely suppressed rage to the point that I could picture him leaping across the room and attacking us if someone so much as dropped a glass.



Grue shook his head.  I think.  I couldn't really tell with the way his darkness shrouded him, with his back turned to us.  He answered, ``Not interested in war, but I'm not going to stop my teammate from doing what she has to.''



``You mean you \emph{can't} stop your subordinate,'' Kaiser mused.



Grue didn't have a quick response to that.  I suspected he couldn't say Bitch wasn't a subordinate without demoting himself in the eyes of the others at the table.  Kaiser, Trickster, Faultline and Coil were all leaders.  Grue took a leadership role when needed, but he wasn't in charge of us.  Not exactly.



Grue clasped his hands in front of him, leaning forward with his elbows on the table. ``It's not so unusual for a cape to have a pet issue.  You should know that as much as anyone.  How would your people react if you forbid them from harassing or hurting gays, Kaiser?''



``I wouldn't.''



``Exactly.  Same with her.  Word gets around that you're someone who hurts dogs, she'll fuck you up.  It's kind of common knowledge here.''



``Not something I'd pay attention to.  I'm more of a cat person.''  The sardonic comment elicited a few chuckles from the room.



``I think it's worth paying attention to if it leads to situations like this,'' Grue responded, his voice firm.



``I delegate to my underlings and trust them to keep track of minor details.  Hookwolf has been out of town until recently.  He must not have heard.''



The bullshit was so transparent I couldn't help but wonder if he was baiting us.



``I'd like to resolve this peacefully,'' Grue reiterated.



Kaiser shook his head with the sound of metal edges scraping on metal, ``Peace is always preferable, but I can't let an insult like this slide.  We'll need restitution before this can be put to rest.  Money or blood.  Your choice.''



Bitch made a sound low in her throat.  She and Hookwolf weren't the only ones bristling.  I looked at the table where Hookwolf sat with Fenja, Menja, Night, Fog, and Krieg, and everyone there looked visibly angry.



``Then let's sit on it until we're freer to give the matter our full attention,'' Grue spoke, ``The truce is in effect, and we'll meet again when things are more or less resolved with the ABB.''  He looked to the others at the table for confirmation.



``We will,'' Coil replied. Faultline nodded.



``What do you say?'' Grue asked Kaiser, ``Set this aside for now?''



Kaiser nodded, once.  ``Fair.  We'll discuss the matter further at our next meeting.''



``That's settled then.  Anything else?'' Coil asked, ``Issues, negotiations, requests?''



There was no reply.



Coil took that as answer enough.  ``Then let's conclude the meeting.  Thank you for attending.  Faultline, could I have a word before you leave?''



There was the sound of chairs scraping against the floor as the people at the table got up, Faultline and Coil excepted.  Skidmark's group headed out the door to leave right away, while Kaiser and Purity walked to the table where their underlings sat with their drinks.  The Travelers loitered around their table, not quite settling in, not leaving.



Grue returned to us, but he didn't sit.



``Let's go.''



Nobody argued.  We stood and left Somer's Rock.  Skidmark's group was taking their time leaving down one end of the street, so, unspoken, we headed in the other direction, just to be safe.  There was no doubt those guys were spoiling for a fight.  They were the diametrical opposite of Kaiser, Coil, and Faultline.  Hotheaded, reckless, unpredictable.  They \emph{would }start a fight, even knowing they would set every other gang in the city against them for abusing neutral territory.



We were a block away from the pub when Grue spoke, ``Bitch.  Do you understand why I'm pissed right now?''



``Why \emph{we're} pissed,'' Tattletale added.



``I guess.''



Grue paused, as if he was choosing his words carefully, ``I want to be \emph{certain} you know what you did wrong.''



``Fuck you,'' she snapped, ``I get the idea.  You don't have to get on my case.''



Grue glanced at the rest of us, then looked over his shoulder in the direction of the pub.



We walked in grim silence past three different stores before he lashed out.  He grabbed Bitch by the shoulder, then pulled her backward to break her stride and put her off balance enough that she stumbled.  Before she could regain her footing, he forced her bodily into the recessed area at the front of an old bookstore and shoved her against the door, his hand gripping her throat.



I looked towards the pub.  There was nobody leaving, and nobody looking our way.  Biting my lip, I joined Tattletale and Regent in stepping inside the alcove.  I was praying Grue knew what he was doing.



For several long seconds, he just held her there, leaving her to claw for a grip on his arm and glove, kick ineffectually at his leg.  Twice, as she looked like she had enough leverage to hit him harder, he used his grip on her throat to pull her forward and then shove her back against the door again, hard enough to give her coughing fits.



She didn't stop fighting as he spoke, his quiet voice hollow with the effects of his power, ``I hate this, Rachel.  That you make me do shit like this.  That when I say things like that, I sound like everything I hate most in this world.  But that's just the way you play things.  It's the only time you're willing to listen.  You hearing what I'm saying?''



Bitch jabbed at the center of his stomach, but he used the length of his arms to pull his body back enough to avoid the worst of the hit, while still holding on to her throat.  He slammed her against the door again.  ``You hearing me, Rachel?''



She nodded sullenly, eyes darting in every direction but directly at him.  He eased up a fraction, and she was able to gasp in a few breaths.



``Look me in the eyes,'' he intoned.



She did.  His visor was just an inch from her face, and she couldn't actually see his eyes, but she stared steadily into the dark holes of his skull mask.  I wasn't sure I could have, and he wasn't angry at \emph{me}.



``You made me look bad.  You made \emph{us} look bad.  I'm not pissed because of what you did to Hookwolf's business.  That's you.  That's your baggage, your shit.  I \emph{get} that it's par for the course with you on the team.  I can live with that.  You following?''



Another reluctant nod.  Not breaking eye contact.



I peeked around the corner to make sure this conversation was still private.  The Travelers were outside the pub now, but they were taking their time leaving.  Trickster was smoking a cigarette through the mouth-hole of his mask.



Grue went on, ``You know what you did wrong?  You didn't fucking tell us.  You let me fucking go in there and talk to those guys and get caught with my pants down.  I had to fucking defend the actions of my team without knowing what the fuck people were talking about.  It made me look weak.  It made \emph{all of us} look weak.''



``You want an apology?''



``Would you mean it?  I haven't heard a honest apology from you since I met you, and believe me, an insincere apology from you would only piss me off \emph{more }right now.  So it's your call.  You want to try?''



Bitch didn't answer.  I could see her square her shoulders, straighten her head, a change of posture that was subtly challenging.



``Christ, Rachel.  This is your second major fuckup in the span of two weeks.  Do I need to talk to the boss and-''



``Stop,'' Tattletale cut in, ``My turn.''



Grue dropped his hand from Bitch's neck and stepped away, folding his arms as he turned his back to her.  What had he been saying before Tattletale interrupted?  \emph{Do I need to talk to the boss and see if we can replace you?}



If that was it, I could see why Tattletale had stepped in.



``You're frustrated, I get it,'' Tattletale spoke.  Bitch was staring in the window of the bookstore, avoiding eye contact while she rubbed her neck.  Tattletale went on, ``You don't feel like you did anything wrong, and if you had another chance to do things over, you feel like you'd do everything the same way\ldots yet people are pissed at you.''



Bitch met Tattletale's eyes.  Her tone was a combination of irritation and boredom, ``And people are taking turns chewing me out and spewing psychobabble shit at me.''



Tattletale waited, maybe to get her composure, to figure out another approach, or to use her power to dig for information she could use.  Or maybe she was waiting to give Bitch time to think about how she wasn't helping herself any with what she was saying.  I wasn't sure – I couldn't read her expression.  She wasn't smiling or grinning like she usually did, though.



Tattletale's tone was more exasperated as she replied, ``Fine.  I'll cut right to the point.  Both of your screwups this past week had to do with a lack of communication.  If you'd called to let us know you were heading out to the money early, maybe we could have anticipated the ambush.  If you let us know you'd messed with Hookwolf's dogfighting ring, we'd have been more prepared tonight.  So open your mouth more.  Talk to us, let us know what's going on.  Alright?''



Bitch didn't respond, tension standing out on her neck, posture stiff, hands in her pockets.



``Think on it,'' Tattletale suggested.



I checked around the corner again.  Trickster was still smoking his cigarette, but he was looking directly at us.  At me.  The gorilla-thing was too, but the others were looking at Trickster.  I think he was talking.  It was hard to tell.



``I think it's time to wrap this up,'' I informed the others, ``Eyes on us.''



We left the nook, with only Bitch's slumped posture giving any indication that anything had gone on.  She trailed a few feet behind the rest of us.  There was tension, and it wasn't all directed at or coming from her.  Grue and Tattletale were walking slightly apart from one another.  He either hadn't liked it when she cut in, or he was angry at himself, but something was bugging one or both of them.



Regent had been quiet throughout.  From what Lisa had said as she visited me earlier in the week, he was still getting twinges of pain from his arm.  I suspected his current state was a combination of painkillers and a lack of a good night's sleep.  He hadn't been a part of the recent dialogue, but his silence wasn't helping the mood any either.



I didn't like this.  This friction spoiling the camaraderie of the group, the undercurrent of tension.  I liked these guys.  Even Bitch, I dunno, I supposed it would be a stretch to say I liked her, but I could maybe respect her for what she brought to the table.



I knew it would be hard to turn on them, to pull off that grand betrayal and turn their information over to the Protectorate, once I had the information I needed\ldots but when I thought on it, I knew I could bite the bullet and do it.  I would have less regrets in the long run.  I could even be proud of it, in the grand scheme of things, maybe.



More and more, I was seeing the day I turned that information over and said goodbye to the Undersiders as the day I wanted to transform myself.  Start transforming Skitter into a hero in the public eye, doing what I could to repair my image, and redefining Taylor into someone confident and outgoing and brave.  If I could cut ties with the Undersiders and take that plunge, I knew I could change myself.



But, strange as it sounded, I would feel \emph{worse }about handing their information to the Protectorate if this sort of negativity was what I was leaving behind when I did it.  I knew it made no sense, but I wanted to be able to tell myself I'd had one successful set of friendships, before I severed ties for the sake of doing the right thing.  I could only hope that the sore feelings would fade.  Even when I'd had friends, it had just been me and Emma.  I didn't have enough experience to really know one way or the other, as far as how groups of friends handled these sorts of sore feelings and resentment.  It sucked.



As I glanced back at Bitch, it struck me that this had to suck worse for \emph{her}.  I felt a twinge of sympathy.



I knew what it felt like, to be the one alone in the midst of a group of people.



Slowing my pace until I was walking beside her, I found myself struggling to find words.  Make small talk?  I wasn't sure how.  Reassure her?  I didn't think I could say anything without seeming like I was siding with her on things, or opening a can of worms as far as getting the argument going again.  Adding my own voice to Grue's and Tattletale's would only make her feel worse, and I had my suspicions she wouldn't stand and take it from me the same way she had with the other two.



``Hookwolf was running a dogfighting ring?'' I asked her, my voice lowered, ``Like, making dogs fight?''



``Fight to the death,'' Bitch answered, almost inaudible.



When your only real companions or family in the world were your dogs, I could see where that hit home.  I'd never had a dog, but the way I saw things, dogs were like kids.  They were at the mercy of specific people, and if those people decided to abuse that, it was just flat out wrong.



``You stopped them?''



She turned her head my way, met my eyes.  ``Made them bleed.''



I felt goosebumps prickle the back of my neck and my arms.  I wasn't sure if I would feel better or worse if she decided to elaborate.



``Good,'' I replied.



We didn't say anything more the rest of the way back.  Probably for the best.





