





There was a long squeal of feedback, followed by the barely audible sound of a man clearing his throat.



``Attention shoppers.  Please be informed that stores will be closing at five-thirty this evening, in cooperation with the city-wide curfew.  Make sure to cooperate with authorities at the entrances and exits of the Weymouth shopping center, and return to your homes by six o'clock.  Thank you.''



The crowd of people that had paused in their conversation and meandering to hear the announcement started moving and talking again, like someone had paused a video and had pressed the play button to get things started once more.



I looked at my dad, ``Should we go?  Beat the last minute rush?''



``Sure.  If there's nothing else you need.''



I was due back at school tomorrow, and my dad had maybe sensed how stressed I was, because he offered to take me shopping.  It felt a little redundant after having been out with Lisa and the guys a week ago, but it did give me the chance to pick up some essentials and to spend some quality time with my dad.



In the bags my dad was holding, I had a new backpack, some notebooks, pens, a half-dozen books, and a new pair of running shoes.  The sort of stuff that I wouldn't have bought with Lisa, because they were so boring, like the notebooks, or because they were the sort of thing I took forever deciding on, like the books and shoes.



All in all, the trip to the mall was a nice gesture, and it somehow meant more to me than Lisa treating me to a few hundred dollars worth of clothes.  Maybe because it was stuff for me.



We made our way to the exit, and I had to hold back a groan.  There was still over half an hour before the doors were due to close, but there was a crush of bodies at the exit.  Maybe half were trying to leave, but the other half were gawking.



Both inside and outside the glass doors of the mall's entrance, there were soldiers.  Their guns were holstered, but they looked pretty intimidating anyways.  In the midst of the soldiers were two capes; Battery and Shadow Stalker.  I knew that members of the Protectorate, the Wards, and various volunteers were stationed at places where there were groups of people, especially in areas in and around the ABB's territory.  The Wards, I supposed, were too young to handle a single location all by themselves, which was probably why Shadow Stalker was in a `sidekick' role here.



I'd had a lot of time to watch the news as I was on bed rest.  Bakuda was living up to what she'd been saying about maximizing fear and panic by combining unpredictability with grim certainty.  Every day, there were reports of anywhere from one to five bombs going off, and while every single one was probably to the advantage of the ABB in some way, there was no way to tell what she'd hit next or why.  One article online had surmised that as the military and superhero presence forced the ABB into a corner, the attacks would only escalate.  Schools, malls and office buildings were all potential targets.  Justification enough for an armed presence here at the mall.



The \emph{upside} was that the mall had organized major sales in pretty much every store, to keep business going.  Maybe not the brightest or most logical thing, but too many businesses and employees were getting by on a day to day basis, around here.



Getting in had been like passing through airport security, getting our bags checked, showing ID.  Nothing too bad.  It had been only Manpower from New Wave standing watch when we arrived, and there hadn't been much of a crowd.  This was something more, two attractive, dangerous heroines, both with some controversy around them.  As much as I could understand why the heroes were here, I could tell they were slowing things down, as the rubberneckers got in the way of the people who were actually leaving.  Half of the military presence that was inside the mall was busy working to keep the crowd back from the doors and the two heroes and trying to organize people into lines.



Progress through the line was slow, but I admit, it was interesting to be able to watch Shadow Stalker and Battery going about their business from a safe perspective.



Battery was a member of the Protectorate.  When I'd been starting junior high, she'd been the head of the Wards for a brief while, and she'd soon after graduated to the Protectorate.  I could guess she was twenty-two or thereabouts now, if they didn't fudge the graduation date or anything to make it harder to guess the hero's real age.  Her power let her charge up as she stood still and concentrated, with every second spent charging giving her a few seconds of greatly enhanced speed, some extra strength and some electromagnetic powers.  Her costume was white and dark gray, with cobalt blue lines tracing it like you might see on a circuit board.  Inquiries about whether her teammate Assault was her boyfriend or her brother had been met with coy deflections, leading a small fraction of the local superhero fans to surmise he was \emph{both}.  Any time she did something in public, you could trust the online message boards to explode with speculation and theory.



That soap-opera/paparazzi style drama had never really grabbed my attention.  Ignoring the vague possibly-maybe chance there was something going on there, I thought she was the kind of hero I could look up to.  She was nice, she worked hard, and in those inevitable situations where she found herself on TV with some asshole getting in her face about something, she handled things rather well.



Battery leaned over to cup her hand over Shadow Stalker's ear and whisper something.  Shadow Stalker nodded and then turned to walk through the glass door to say something to the soldiers stationed outside.  Literally \emph{through} the door.  As she did it she turned a little smoky, like she was made of sand and not anything solid.  It didn't seem constructive to me.  In her shoes, I think I would have stuck to business as usual, without giving them more reason to stare – I would have used a door normally.



Maybe I was biased.  I kind of felt like I should dislike or hate her on principle, since she was Grue's self-declared nemesis.  Lisa and Alec had explained how Shadow Stalker was a vigilante that agreed to join the Wards rather than jail, after going too far in the pursuit of justice.  She was \emph{supposed} to be using nonlethal weapons, but she wasn't.



Capes always seemed so much bigger and impressive on the news.  Once you looked past the dark gray urban-camouflage hood and cape, and the black-painted metal of her mask, Shadow Stalker was still just a teenage girl.  Only about as tall as me.  Battery was only two or so inches taller than either Shadow Stalker or myself, which meant she was still shorter than most of the men in the crowd.  Now that I had been involved in cape stuff, I felt like I could look past the costume in a way most didn't.  They looked normal, pretty much.



``Alan,'' my dad spoke, ``It's been a long time.''



I turned to look.  I should have been surprised, or shocked, but by the time I realized who we'd run into, I felt too deflated.



``It's good to see you, Danny.  I've been meaning to get in touch.''



``Not a problem, not a problem,'' my dad laughed easily.  He shook the hand of the red cheeked, red haired man.  Alan Barnes.  ``These days, we can count it as a good thing if we're busy.  Is your daughter here?''



Alan looked around, ``She was thirsty, so I'm holding our place in line while she\ldots ah, here she is.''



Emma joined us, a diet sprite in one hand.  She looked momentarily surprised as she saw me.  Then she smiled, ``Hi Taylor.''



I didn't reply.  A few moments of awkward silence lingered.



``We need to get back in touch, Danny,'' Emma's dad smiled, ``Maybe you could come over for a barbecue sometime.  When it's a little warmer, the weather will be perfect for it.''



``I'd like that,'' my dad agreed.



``How's work?



``Better and worse.  There's work to be had for the Dockworkers, with cleanup, reconstruction efforts, so that's good.''



``And your projects?  The ferry?''



``I've resigned myself to waiting a few more months before I start making noise again.  Mayoral elections are this coming summer, and there will be elections for the city council this fall.  I'm hoping to see some fresh faces, people who won't dismiss some revival efforts as options.''



``I wish you luck, then.  You know my firm is there if you need us.''



``Appreciated.''



Emma turned her attention from idly watching the heroes and army at work to our dads' conversation.  My dad saw her looking his way and decided to include her in the conversation.



``So.  Is Emma still modeling?''



``She is!'' Alan smiled proudly, ``And doing quite well, but that's not why we're here today.  We were just here for the sales,'' Alan chuckled a little, ``My daughter wouldn't let me relax the second she heard about it.''



``Ah.  Us too.  Shopping, I mean.  Taylor was caught at the edge of one of the explosions, around the time this whole scene started,'' my dad answered, ``She's been home for a week recuperating.  I thought we'd go shopping before she got back into the swing of things.''



``Nothing serious in the way of injuries, I hope?'' Alan asked.



``I'm in one piece,'' I answered, not taking my eyes off Emma.



``That's good.  My god, you're the third person I know who's been affected by this anarchy.  One of my partners is in recovery from surgery.  An explosion crystallized his arm, turned it to glass.  Terrifying.'' Alan told my dad, ``When does this end?''



While our dads talked, Emma and I just stared at each other.



Then Emma smiled.  It was a look I'd seen so many times in the past few years.



It was the smile that had greeted me when I came back to school from the hospital, back in January, that look that let me know she wasn't done.  The same expression she'd had when she was looking down on me, covered in juice and cola in the stall of the school bathroom.  The one she'd been wearing when I'd come out of the showers to find my clothes crammed in the toilets, both my gym clothes and regular ones.



The same smile she'd had before she reminded me of how my mom had died, in front of everyone.



The sound of the impact was like a splash of water in my face.  I felt a twinge of pain from that gouge one of Bitch's dogs had made in my arm, when I first met her.  Still sore.



Emma fell over, bumping into her dad, who dropped the bags he was holding.  There were gasps from the crowd around us.



``Taylor!'' My dad cried out, aghast.



My hand was stinging.  Outstretched in front of me, like I was reaching out to shake someone's hand.  It took me a seconds to connect the dots.  I'd hit her?



Emma looked up at me, eyes wide, mouth open, one hand to the side of her face.  I was as shocked at what I'd done as she was.  Not that I felt \emph{bad}.  A large part of me wanted to laugh in her face.  Weren't expecting that?  Miscalculated how I'd react?



Hands seized me with an iron grip and spun me around.  Shadow Stalker.  She interposed herself between me and Emma.  Dark brown eyes glowered at me from behind her mask.



``What was that for?!'' Alan protested, ``Emma didn't even \emph{say} anything!''



``I'm so sorry,'' my dad hurried to explain to the superheroine and Emma's dad, ``She's still recovering from a concussion, it's affected her mood.  I didn't expect anything this extreme.''



Shadow Stalker scolded him, ``This is \emph{not} the time or place for arguments.  If your daughter is this\ldots unwell, then that's \emph{your} responsibility.''



I felt like laughing.  Part of it was just being giddy at doing something to get back at Emma.  The other part was that this whole scenario was so ridiculously upside-down.  Shadow Stalker wasn't really anything special.  She was just a \emph{teenage girl}, lecturing my dad, an adult.  The crowd that was watching was seeing Emma as the victim, me as the bad guy.  But if you stripped away the costume, if everyone knew the real story, this would all be playing out so differently.  Emma would be the bad guy, and my dad wouldn't be so conciliatory about this girl telling him off.



I had the presence of mind to not laugh aloud.  Maybe it was the adrenaline, the relief that flowed from what I'd just done.  Maybe it was the concussion, again, but I did find the conviction to do something else.



I pointed at Emma, turned to my dad, ``You want to know why I hit her?''



Shadow Stalker put one hand on the side of my face, forced me to look at her, stopping me from talking in the process. ``No.  I'm stopping this right here.  No arguments, no excuses as to why you just assaulted someone.  We're breaking this up now.  Turn around.''



``What?'' I half-laughed, incredulous, ``Why?''



``Taylor,'' my dad said, looking drained, ``Do as she says.''



It didn't really matter, because she forced me to turn around anyways, wrenching my arm until I did, then pulling my arms behind my back.



``Please, miss,'' my dad said, ``This isn't necessary.''



Shadow Stalker bound my wrists with what I guessed was a plastic wrist-tie.  Too tight.  Then she turned to my dad, and her voice was hushed.  ``Look at this crowd.  These people.  They're \emph{scared}.  A place like this, with this much suppressed panic, fear and worry, this many people close together?  I don't care if your daughter is an idiot or just ill.  She's proven to be volatile in a powder-keg situation.  It's both dangerous and \emph{stupid} to have her here.  You can cut off the plasti-cuffs when she's separated from anyone she might harm.''



``I'm \emph{not} dangerous,'' I protested.



``Didn't look like it to me.'' Shadow Stalker shook her head and gave me a push towards the exit, ``Go home and be grateful your dad isn't having to post bail for you to sleep in your own room tonight.''



My dad held his bags with one hand so he could help usher me toward the door.  He looked over his shoulder at Alan, ``I'm very sorry.  It's the concussion.''



Alan nodded, sympathetic.  His ruddy cheeks were redder at the attention our scene had drawn, ``I know.  It's alright.  Just\ldots maybe she should stay home from school for a bit longer.''



My dad nodded, embarrassed.  I felt bad at that.  I felt worse at being led off like a criminal, while Shadow Stalker gave Emma a hand to help her up.  Emma was beaming, smiling one of the widest smiles I'd seen her give, despite the red mark on the side of her face.  Smiling as much at the way things had turned out, I imagined, as she was at getting the chance to talk with the concerned superheroine.



We headed out to the car, away from the crowd, the soldiers and Emma.  I stood by the open passenger door for two minutes before my dad scrounged up some nail clippers to cut off the plasti-cuffs.



``I'm not mad,'' he told me, quietly, after we'd settled in, as he started up the car and took us out of the parking garage.



``Okay.''



``It's perfectly understandable.  You're emotionally sensitive, after getting knocked around by the explosion, and she reminds you of what's going on at school.''



``More than you know,'' I muttered.



``Hm?''



I looked down at my hands, rubbed my wrists where the plastic tie had cut into them.



If I didn't tell him now, I don't think I ever would.



``It's her.  Emma.''



``Oh?  What?'' He sounded confused.



I didn't have it in me to clarify matters.  I just let him think it over.



After a long pause, he just said, ``Oh.''



``From the beginning. Her and her friends,'' I added, needlessly.



Tears welled up, unexpected.  I hadn't even realized I felt like crying.  I raised my glasses to rub them away, but more came streaming out.



``Stupid head injury,'' I mumbled, ``Stupid mood swings.  I'm supposed to be better by now.''



My dad shook his head, ``Taylor, kiddo, I don't think it's the only reason.''



He pulled over.



``What are you doing?'' I asked, wiping ineffectually at my cheek, ``We gotta be home before the curfew.''



He undid our seat belts and pulled me into a hug, my face against his shoulder.  My breath hitched with a sob.



``It's fine,'' he assured me.



``But--''



``We've got time.  Take as long as you need.''





