





A huge pet peeve of mine: being asked to arrive for a specific time, then being made to wait.  Fifteen minutes was just about my limit of my patience.



My dad and I had been waiting for more than thirty minutes.



``This has to be intentional,'' I complained.  We'd been asked to wait in the principal's office a few minutes after we arrived, but the principal hadn't been around.



``Mmm.  Trying to show they're in a position of power, able to make us wait,'' my dad agreed, ``Maybe.  Or we're just waiting for the other girl.''



I was at an angle where if I slouched in my chair just a bit, I could see the front of the office through a gap between the bottom of the blinds and the window.  Not long after we'd arrived, Emma and her dad had showed up, looking totally casual and unstressed, like it was a regular day.  \emph{She isn't even worried}.  Her dad was her physical opposite, beyond the red hair they shared – he was big in every sense of the word.  Taller than average, big around the middle, and while he could speak softly when the situation called for it, he had a powerful voice that caught people's attention.  Emma just had a biggish chest.



Emma's dad was talking to Madison's mom and dad.  Only Madison's mom was really petite like she was, but both her mom and dad looked really young.  Unlike Emma and her dad, Madison and her parents did look concerned, and I was guessing that some of what Emma's dad was doing was reassuring them.  Madison in particular was looking down at the ground and not really talking, except to respond to what Emma was saying.



Sophia was the last to arrive.  She looked sullen, angry, an expression that reminded me of Bitch.  The woman who accompanied her was most definitely not her mom.  She was blond and blue eyed, had a heart shaped face and wore a navy blue blouse with khakis.



The secretary came to get us from the office not long after.



``Chin up, Taylor,'' my dad murmured, as I slung my backpack over one shoulder, ``Look confident, because this won't be easy.  We may be in the right, but Alan's a partner in a law firm, he's a master manipulator of the system.''



I nodded.  I was getting that impression already.  After getting a phone call from my dad, \emph{Alan }had been the one to call this meeting.



We were directed down the hall to where the guidance counselor's offices were, a room with an egg-shaped conference table.  The trio and their guardians were seated at one end of the table, seven in total, and we were asked to sit at the other, the tip of the egg.  The principal and my teachers all came into the room not long after, filling in the seats between us.  Maybe I was reading too much into things after seeing an eerie echo of this situation just two days ago, with the meeting of villains, but I noted that Mr. Gladly sat next to Madison's dad, and the chair next to my dad was left empty.  We would have been completely isolated from the mass of people at the other side of the table if Mrs. Knott, my homeroom teacher, hadn't sat at my left.  I wondered if she would have, if there'd been another seat.



I was nervous.  I had told my dad that I'd missed classes.  I hadn't told him how many, but I hadn't wanted to repeat Bitch's mistake and leave him totally in the dark.  I was worried it would come up.  Worried this wouldn't go the way I hoped.  Worried I'd find some way to fuck it up.



``Thank you all for coming,'' the principal spoke, as she sat down, putting a thin folder down in front of her.  She was a narrow woman, dirty blond, with that severe bowl-cut haircut I could \emph{never} understand the appeal of.  She was dressed like she was attending a funeral – black blouse, sweater and skirt, black shoes, ``We're here to discuss incidents where one of our students has been victimized.''  She looked down at the folder she'd brought in, ``Ms. Hebert?''



``That's me.''



``And the individuals accused of misconduct are\ldots  Emma Barnes, Madison Clements and Sophia Hess.  You've been in my office before, Sophia.  I just wish it had more to do with the track and field team and less to do with detention.''



Sophia mumbled a reply that might have been agreement.



``Now, if I'm to understand matters, Emma was attacked outside of school premises by Ms. Hebert?  And shortly after, she was accused of bullying?''



``Yes,'' Alan spoke, ``Her father called me, confronted me, and I thought it best to take this to official channels.''



``That's probably best,'' the principal agreed.  ``Let's put this matter to rest.''



Then she turned to me and my dad, palms up.



``What?'' I asked.



``Please.  What charges would you lay against these three?''



I laughed a little, in disbelief, ``Nice.  So we're called here on short notice, without time to prepare, and I'm expected to be ready?''



``Maybe outline some of the major incidents, then?''



``What about the minor ones?'' I challenged her, ``All of the little things that made my day-to-day so miserable?''



``If you can't remember-''



``I remember,'' I cut her off.  I bent down to the backpack I'd set at my feet and retrieved a pile of paper.  I had to flip through it for a few seconds before I could divide it into two piles.  ``Six vicious emails, Sophia pushed me down the stairs when I was near the bottom, making me drop my books, tripped and shoved me no less than three times during gym, and threw my clothes at me while I was in the shower after gym class had ended, getting them wet.  I had to wear my gym clothes for the rest of the morning.  In biology, Madison used every excuse she could to use the pencil sharpener or talk to the teacher, and each time she passed my desk, she pushed everything I had on my desk to the floor.  I was watching for it the third time, and covered my stuff when she approached, so on the fourth trip, she emptied the pencil sharpener into one of her hands and dumped the shavings onto my head and desk as she walked by.  All three of them cornered me after school had ended and took my backpack from me, throwing it in the garbage.''



``I see,'' the principal made a sympathetic face, ``Not very pleasant, is it?''



``That's September eighth,'' I pointed out, ``My first day back at school, last semester.  September ninth-''



``Excuse me, sorry.  How many entries do you have?''



``One for pretty much every school day starting last semester.  Sorry, I only decided to keep track last summer.  \emph{September ninth}, other girls in my grade had been encouraged by those three to make fun of me.  I was wearing the backpack they had been thrown in the trash, so every girl that was in on it was holding their nose or saying I smelled like garbage.  It picked up steam, and by the end of the day, others had joined in on it.  I had to change my email address after my inbox filled in just a day, with more of the same sorts of things.  I have every hateful email that was sent to me here, by the way.''  I put my hand on the second pile of papers.



``May I?'' Mrs. Knott asked.  I handed her the emails.



``Eat glass and choke.  Looking at you depresses me.  Die in a fire,'' she recited as she turned pages.



``Let's not get sidetracked,'' my dad said, ``We'll get to everything in time.  My daughter was speaking.''



``I wasn't done with September ninth,'' I said, ``Um, let me find my place.  Gym class, again-''



``Are you wanting to recount every single incident?'' the principal asked.



``I thought you'd want me to.  You can't make a fair judgment until you hear everything that's happened.''



``I'm afraid that looks like quite a bit, and some of us have jobs to get back to later this afternoon.  Can you pare it down to the most relevant incidents?''



``They're \emph{all}` relevant,'' I said.  Maybe I'd raised my voice, because my dad put his hand on my shoulder.  I took a breath, then said, as calmly as I could, ``If it bothers you to have to listen to it all, imagine what it feels like to live through it.  Maybe you'll get just a fraction of a percent of an idea of what going to school with \emph{them} felt like.''



I looked at the girls.  Only Madison looked really upset.  Sophia was glaring at me, and Emma managed to look bored, confident.  I didn't like that.



Alan spoke, ``I think we all grasp that it's been unpleasant.  You've established that, and I thank you for the insight.  But how many of those incidents can you \emph{prove}?  Were those emails sent from school computers?''



``Very few school email addresses, mostly throwaway accounts from hotmail and yahoo,'' Mrs. Knott replied, as she flipped through the pages, ``And for the few school email accounts that \emph{were }used, we can't discount the chance that someone left their account logged in when they left the computer lab.''  She gave me an apologetic look.



``So the emails are off the table,'' Alan spoke.



``It's not your place to decide that,'' my dad answered.



``A lot of those emails were sent during school hours,'' I stressed.  My heart was pounding.  ``I even marked them out with blue highlighter.''



``No,'' the principal spoke, ``I agree with Mr. Barnes.  It's probably for the best that we focus our attention on what we can verify.  We can't say who sent those emails and from where.''



All of my work, all of the hours I'd put in logging events when remembering the events of the day was the last thing I wanted to do, dashed to the winds.  I clenched my fists in my lap.



``You okay?'' my dad murmured in my ear.



There was precious little I could actually verify, though.



``Two weeks ago, Mr. Gladly approached me,'' I addressed the room, ``He verified that some things had occurred in his class.  My desk had been vandalized with scribbles, juice, glue, trash and other stuff on different days.  Do you remember, Mr. Gladly?''



Mr Gladly nodded, ``I do.''



``And after class, do you remember seeing me in the hallway?  Surrounded by girls?  Being taunted?''



``I remember seeing you in the hallway with the other girls, yes.  If I remember, that was not long after you told me you wanted to handle things on your own.''



``That is \emph{not} what I said,'' I had to control myself to keep from shouting, ``I said I thought \emph{this} situation here, with all the parents and teachers gathered, would be a farce.  So far, you're not proving me wrong.''



``Taylor,'' my dad spoke.  He put his hand on one of my clenched fists, then addressed the faculty, ``Are you accusing my daughter of making up everything she's noted here?''



``No,'' the principal spoke, ``But I think that when someone is being victimized, it's possible to embellish events, or to see harassment when there is none.  We want to ensure that these three girls get fair treatment.''



``Do \emph{I-}'' I started, but my dad squeezed my hand, and I shut up.



``My daughter deserves fair treatment too, and if even one in ten of these events did occur, it speaks to an ongoing campaign of severe abuse.  Does anyone disagree?''



``Abuse is a strong word,'' Alan spoke, ``You still haven't \emph{proven-``}



``Alan,'' my dad interrupted him, ``Please shut up.  This isn't a courtroom.  Everyone at this table knows what these girls did, and you can't force us to ignore it.  Taylor ate dinner at your dining room table a hundred times, and Emma did the same at ours.  If you're implying Taylor is a liar, say it outright.''



``I only think she's sensitive, especially after the death of her mother, she-''



I shoved the pile of paper off the table.  There were thirty or forty sheets, so it made a good size cloud of drifting papers.



``Don't go there,'' I spoke, quiet, I could barely hear myself over the buzzing in my ears, ``Don't do that.  Prove you're at least that human.''



I saw a smirk on Emma's face, before she put her elbows on the table and hid it with her hands.



``In January, my daughter was subjected to one of the most malicious, disgusting pranks I have ever \emph{heard} of,'' my dad told the principal, ignoring the papers that were still making their way to the floor, ``She wound up in the hospital.  You looked me in the eye and promised me you would look after Taylor and keep an eye out.  You obviously haven't.''



Mr. Quinlan, my math teacher, spoke, ``You have to understand, other things demand our attention.  There's a gang presence in this school, and we deal with serious events like students bringing knives to class, drug use, and students suffering life threatening injuries in fights on the campus.  If we're not aware of certain events, it's hardly intentional.''



``So my daughter's situation isn't serious.''



``That's not what we're saying,'' the principal answered him, exasperated.



Alan spoke, ``Let's cut to the chase.  What would you two like to see happen, here, at this table, that would have you walk away satisfied?''



My dad turned to me.  We'd talked briefly on this.  He'd said that as a spokesperson for his Union, he always walked into a discussion with a goal in mind.  We'd established ours.  The ball was in my court.



``Transfer me to Arcadia High.''



There were a few looks of surprise.



``I expected you to suggest expulsion,'' the principal answered, ``Most would.''



``Fuck no,'' I said.  I pressed my fingers to my temples, ``Sorry for swearing.  I'm going to be a little impulsive until I'm over this concussion.  But no, no expulsion.  Because that just means \emph{they} can apply to the next-closest school, Arcadia, and because they aren't enrolled in school, it would mean accelerated entry past the waiting list.  That's just rewarding them.''



``Rewarding,'' the principal spoke.  I think she was insulted.  Good.



``Yeah,'' I said, not caring in the least about her pride, ``Arcadia's a good school.  No gangs.  No drugs.  It has a \emph{budget}.  It has a reputation to maintain.  If I were bullied there, I could go to the faculty and get help.  \emph{None} of that's true here.''



``That's all you would want?'' Alan asked.



I shook my head, ``No.  If it were up to me, I'd want those three to have in-school suspension for the remaining two months of the semester.  No privileges either.  They wouldn't be allowed dances, access to school events, computers, or a spot on teams or clubs.''



``Sophia's one of our best runners in Track and Field,'' the principal spoke.



``I really, really don't care,'' I replied.  Sophia glared at me.



``Why in-school suspension?'' Mr. Gladly asked, ``It would mean someone would have to keep a constant eye on them.''



``Would I have to take summer classes?'' Madison piped up.



``There would be remedial classes if we took that route, yes,'' the principal spoke, ``I think that's a little severe.  As Mr. Gladly mentioned, it would require resources we don't have.  Our staff is stretched thin as it is.''



``Suspension's a vacation,'' I retorted, ``and it just means they could take a trip over to Arcadia and get revenge on me there.  No.  I'd rather they got no punishment at all than see them get suspended or expelled.''



``That's an option,'' Alan joked.



``Shut up, Alan,'' my dad replied.  To the rest of the table, he said, ``I don't see anything unrealistic about what my daughter is proposing.''



``Of course you don't,'' Sophia's guardian spoke, ``You'd feel differently if the tables were turned.  I feel it's important that Sophia continue to attend her track and field practices.  The sports give her structure she needs.  Denying her that would only lead to a decline in her behavior and conduct.''



Madison's dad added his own two cents, ``I think two months of suspension is too much.''



``I'm forced to agree on all counts,'' the principal spoke.  As my dad and I moved to protest, she raised her hands to stop us, ``Given the events that happened in January, and with Mr. Gladly's own admission that there's been incidents in his class, we know there's been some ongoing bullying.  I'd like to think my years as an educator have given me some ability to recognize guilt when I see it, and I'm certain these girls are guilty of \emph{some} of what the victim is accusing them of.  I'm proposing a two week suspension.''



``Weren't you listening to me?'' I asked.  My fists were clenched so hard my hands were shaking, ``I'm not asking for a suspension.  That's pretty much the last thing I want.''



``I'm standing by my daughter in this,'' my dad spoke, ``I'd say two weeks was laughable, given this laundry list of \emph{criminal} offenses these girls have committed, except there's nothing funny about this.''



``Your list would mean something if you could back it up with \emph{evidence,'' }Alan wryly commented, ``And if it wasn't all over the floor.''



I thought for a second that my dad would hit him.



``Any longer than two weeks would mean these girls' academics would suffer to the point they could fail the year,'' the principal stated, ``I don't think that's fair.''



``And \emph{my} schoolwork hasn't suffered because of them?'' I asked.  The buzzing in my ears was reaching its limit.  I realized, belatedly, that I'd just given her an opening to raise my missed classes.



``We're not saying it hasn't,'' the principal's tone was patient, as if she was talking to a small child.  ``But eye-for-an-eye justice doesn't do anyone any favors.''



She hadn't mentioned the classes.  I wondered if she even knew.



``Is there \emph{any }justice here?'' I replied, ``I'm not seeing it.''



``They're being punished for their misconduct.''



I had to stop to willfully \emph{push} the bugs away.  I think they were reacting to my stress, or my concussion was making me a little less aware of what I was doing with them, because they were pressing in without my giving them the order.  None had entered the school or the conference room, thankfully, but I was getting increasingly worried that my control would slip.  If it did, instead of sort of wandering in my general direction or gravitating towards my location, the bugs would erupt into a full fledged swarm.



I took a deep breath.



``Whatever,'' I said, ``You know what?  Fine.  Let them get away with a two week vacation as a reward for what they did to me.  Maybe if their parents have an ounce of heart or responsibility, they'll find an appropriate punishment.  I don't care.  Just transfer me to Arcadia.  Let me walk away from this.''



``That's not really something I can do,'' the principal said, ``There's jurisdictions-''



``\emph{Try},'' I pleaded, ``Pull some strings, call in favors, talk to friends in other faculties?''



``I don't want to make any promises I can't keep,'' she said.



Which meant no.



I stood up.



``Taylor,'' my dad put his hand on my arm.



``We're not the enemy,'' the principal spoke.



``No?'' I laughed a little, bitter, ``That's funny.  Because it looks like it's you guys, the bullies and the other parents against me and my dad.  How many times have you called me by my \emph{name}, today?  None.  Do you even know why?  It's a trick lawyers use.  They call their client by name, but they refer to the other guy as the victim, or the offender, depending.  Makes your client more identifiable, dehumanizes the other side.  He started doing it right off the bat, maybe even before this meeting started, and you unconsciously bought into it.''



``You're being paranoid,'' the principal spoke, ``Taylor.  I'm sure I've said your name.''



``Fuck you,'' I snapped, ``You disgust me.  You're a deluded, slimy, self-serving-''



``Taylor!'' my dad pulled on my arm, ``Stop!''



I had to concentrate a second and direct the bugs to go away, again.



``Maybe I'll bring a weapon to school,'' I said, glaring at them, ``If I threatened to stab one of those girls, would you at least expel me?  Please?''  I could see Emma's eyes widen at that.  Good.  Maybe she'd hesitate before hassling me again.



``Taylor!'' my dad spoke.  He stood up and pulled me into a tight hug, my face against his chest so I couldn't say any more.



``Do I need to call the cops?'' I heard Alan.



``For the last time, Alan, shut up,'' my dad growled, ``My daughter is right.  This has been a joke.  I have a friend in the media.  I think I'm going to give her a call, email her that list of emails and the list of incidents.  Maybe pressure from the public would get things done.''



``I hope it doesn't come to that, Danny,'' Alan replied, ``If you recall, your daughter assaulted and battered Emma just last night.  That's in addition to threatening her, here.  We could press charges.  I \emph{do} have the surveillance video from the mall, and a signed slip from that teenage superheroine, Shadow Stalker, that verifies she saw it happen, in what could have provoked a riot.''



Oh.  So that was why Emma had been so confident.  She and her dad had an ace up their sleeve.



``There's mitigating circumstances,'' my dad protested, ``She has a concussion, she was provoked, she only hit Emma once.  The charges wouldn't stick.''



``No.  But the case could drag out for some time.  When our families used to have dinner together, you remember me saying how most cases were resolved?''



``Decided by who ran out of money first,'' my dad said.  I felt him clutch me a fraction tighter.



``I may be a divorce attorney, but the same applies in a criminal case.''



If we went to the media, he'd press assault charges just to drain our bank accounts.



``I thought we were friends, Alan,'' my dad replied, his voice strained.



``We were.  But at the end of the day, I have to protect my daughter.''



I looked at my teachers.  At Mrs. Knott, who I'd even say was my favorite teacher, ``Don't you see how fucked up this is?  He's blackmailing us right in front of you, and you can't understand that this manipulation has been going on from the beginning?''



Mrs. Knott frowned, ``I don't like the sound of it, but we can only comment and act on what happens in school.''



``It's happening right here!''



``You know what I mean.''



I pulled away.  In my haste to get out of that room, I practically kicked down the door.  My dad caught up to me in the hallway.



``I'm sorry,'' he said.



``Whatever,'' I said, ``I'm \emph{so} not surprised.''



``Let's go home.''



I shook my head, turning away, ``No.  I need to get gone.  Going.  I won't be home for dinner.''



``Stop.''



I paused.



``I want you to know I love you.  This is far from over, and I'll be waiting for you when you come home.  Don't give up, and don't do anything reckless.''



I hugged my arms close to my body to get the shaking in my hands to stop.



```Kay.''



I left him behind and headed out the front door of the school.  Double checking he hadn't followed and that he couldn't see me, I retrieved one of the disposable cell phones from the front pocket of my sweatshirt.  Lisa picked up partway through the first ring.  She always did – one of her little quirks.



``Hey.  How did it go?''



I couldn't find the words for a reply.



``That bad?''



``Yeah.''



``What do you need?''



``I want to hit someone.''



``We're gearing up for a raid on the ABB.  We didn't bother you about it because you're still recovering, and I knew you'd be busy with your meeting at school.  Want in?''



``Yeah.''



``Good.  We're splitting up for a bunch of coordinated attacks with some of the other groups.  You'd be with, um, one second-''



She said something, but it wasn't directed at the phone.  I heard the bass of Brian replying.



``Every team is splitting up, bit complicated to explain, but yeah.  Bitch would be going with one or two members of the Travelers, some of Faultline's crew and probably some of Empire Eighty-Eight.  It would do a lot for our peace of mind if you went with.  `specially with the tension between us and the Empire.''



I could see the bus at the far end of the street, approaching.



``I'll be there in twenty minutes.''





