





Time was short, so Tattletale was in my room of the loft while I changed.



``The idea Coil proposed was that we would mix and match the members of the groups, so nobody can pull anything without their teammates being hostage to the other groups.''



``Gotcha,'' I replied.  I busied myself double checking the items from the utility compartment.  Tattletale reached in and snatched the cell phone.  ``Hey?''



``One sec.  I'm programming the alarm on your phone.  When it goes off, an hour from now, you call Grue.  Then again an hour later, if we're out that long.  We'll all be checking in with each other every fifteen minutes or so.  If someone doesn't pick up, assume they're in trouble.''



``Okay,'' I agreed.



``If you can't pick up the phone for whatever reason, be sure to call back at the first opportunity.  Let us know you're fine.''



``Got it.''  I hiked the cloth portion of my armor up around my waist, then began sliding my arms through the sleeves.  The cloth part was form-fitting, and all in all, putting it on was like putting on a pair of full-body pantyhose.  Not prone to tear, of course, but like the pantyhose, it always took longer than I expected.



``We'll be using a password system every time we check in, in case you're taken hostage and forced to answer a call.  Two parts to it.  The first part is simple, you give the other person the first letter of one of our names, the other person replies with the last.  If it winds up being a longer night, move on to other people we know.''



``So if I said L?''



``A.  How would you respond to B?''



``N.''



``Exactly.  The second part is color based.  When you're replying to a call, name an object that's a certain color.  Think traffic lights.  Green for go, everything is okay.  Yellow for warning, if you aren't sure about things.  Red for stop, need help.  It lets you keep us informed without tipping off the capes that are with you.''



``Okay.''



``I'm going with the group that has Faultline, Trickster, and the Traveller's shapeshifter.  I'm betting there will be a few from Empire Eighty-Eight and some of Coil's soldiers, too.''



``Shapeshifter?''



``That gorilla with four arms, from the other night.  Only I don't know exactly what she is, yet, but she's not quite a shapeshifter.  I'm hoping to get a better sense of her abilities by spending some time around her.  Ditto for Trickster.  Regent's coming with so we're contributing \emph{some} firepower.  Kind of.''



``Don't you and Faultline have issues with each other?''



Lisa grinned, ``Yup.  It's going to be fun, pushing her buttons, knowing she can't touch me.''



I winced.  ``Just be careful.  What's Grue doing?''



``Another group.  All in all, we'll be coordinating to strike three locations simultaneously with three different teams, overwhelming force.  Hit hard, hit fast, get out of there.  If you aren't making much of a dent, don't sweat it.  Unless something goes horribly wrong, we'll repeat this process a few more times over the next couple of days.''



There was a knock on the door.  Brian called from the other side, ``Just about ready?''



I zipped up the back of my costume and strapped my armor in place over it, then opened the door, mask in one hand, ``Ready.''



Brian, like me, was costumed but didn't have any headgear on.  ``You sure you're up to this?  You're recovered from the knock you took to the head?''



``No,'' I admitted, ``Not entirely.  But I'm pissed, and I think I'll be \emph{less} okay in the long run if I don't go out and vent somehow.''



He paused, as if he were thinking things over, ``Okay.  You going to be alright dealing with Bitch on your own?''



I frowned, ``I'll manage somehow.''



``Don't show her any weakness, or she won't let up on you.''



``I figured as much,'' I agreed.  As we headed for the stairs, I mused that maybe Bitch and I were more on the same page today.  I was pissed at life in general, feeling just a bit off kilter in a way that wasn't one-hundred-percent the concussion.



I pulled on my mask as we headed outside.  There was a nondescript van pulled over in front of the door, blocking line of sight to the rest of the street.  Bitch and Regent were already inside, waiting.



``Hey dork,'' Regent greeted me.  He was in costume, typical except for the shirt he was wearing – other nights it had been white, but it was a dark gray today.  It was still the same slightly elaborate, puffy renaissance fair style of clothing, though.



``You can call me Skitter.  I won't mind.''



``That's alright,'' he answered.  There was a note of humor in his voice, which I took to mean he was just having fun at my expense.  I resolved to ignore him.



Bitch just stared angrily at me.  It was so intense I had to look away.  So much for being on the same page.



The interior of the van had benches on either side.  Since we were in a rush, I had only a second to decide whether I wanted to sit next to Regent – and be facing Bitch for the duration of the trip – or plop myself down next to her and the dogs.  I opted for the former, hoping I wouldn't manage to do or say anything that would get us off on a bad start for the evening.



Tattletale sat in the passenger seat, with Grue driving.  As the van pulled onto the road, she called back to us, ``Hey, Bitch, Skitter.  We're dropping you off first, but you're going to have to walk to the meeting place.  You might be short on time, so walk fast.  Cool?''



Bitch shrugged, ``Works.''



``No complaints,'' I added my own two cents.  I could see where it would be advantageous – Bitch would have time to get her dogs beefed up, and I could gather some bugs.  Besides, it gave us something to do – if we had to stand idle for a few minutes, I was pretty sure it would only increase the chances of Bitch finding a reason to pick a fight with me or one of the other villains.



Remembering my bugs, I took a few seconds to extend my powers outward and begin gathering them.  I was surprised at how far my reach was extending.  I generally measured things in city blocks – I've never been good at eyeballing distance – and I would say my range usually sat at around two blocks.  Today I was reaching just shy of three and a half.



``Hey Tattletale?'' I asked.



``Sup?''



``Two questions.''



``Go for it.''



``What general direction is the spot you're dropping me off?  Need to know where to send the bugs.''



``Northwest.''



I glanced out the tinted windows of the van to judge which direction we were going, then began giving commands to the bugs that fell within my reach.



``Second question.  Um.  My power's a fair bit stronger today.  Not sure about technique, but I'm extending a lot further.  Any idea why?''



``Can't say.  Sorry, I could usually try to figure it out, but I'm focusing on other things right now.  If you think it's really crucial--''



``No,'' I stopped her, ``It's not.  I'll bug you about it later, when your attention isn't divided.''



``Pun intended?'' Regent mused.



``What?''



``Guess not.  Nevermind,'' he chuckled a little.



Bitch was using her power on her dogs.  It was really my first opportunity seeing it happen from the beginning.  It was like seeing a sausage split its casing, only the casing was fur and skin.  Where the rifts appeared, it wasn't just muscle spilling out, but spears and ridges of bone.  Some of the exposed muscle shriveled into scaly growths.  Yet they kept growing to the point the back of the van was feeling crowded.  Where did that mass come from?  Was it pulled out of thin air, or was she drawing in some kind of energy and converting it into matter?



For that matter, if my brain was a radio tower of sorts, pinging every bug for their locations on a near-constant basis and sending them instructions to override their own brains\ldots where was the energy to keep \emph{that} up coming from?



It was a little disconcerting to think about.



When Grue stopped the van to let us out, I realized why we were walking.  Our stop was a bridge with bus stations on either side.  Problem was, it seemed the ABB had decided to cut off this route – the bridge had been reduced to rubble.  Large orange and black detour signs with blinking lights barred entry to the shattered bridge, and similar measures had been used to cordon off the piles of rubble below.



Tattletale leaned out the open window and pointed, ``See that tower, there?  Looks like a lighthouse?  It's an old tourist shop that closed down a decade ago.  It's where the Merchants – Skidmark and his crew of dealers – hung out, before the ABB expanded and forced them out.  You're supposed to meet the others there.''



I looked and saw the building she was pointing at.  It didn't look much like a lighthouse, but whatever.  ``Gotcha.''



``Go,'' Brian said, ``Good luck.''



Bitch whistled for her dogs, and we headed for the stairs.  We'd have to head down, across the street and back up to get where we needed to be.



It was weird, picking our way through the rubble of the destroyed bridge to cross the street.  You didn't usually cross the road like this, and the streets were deserted here.   The dogs seemed to like the experience though.  I saw Judas' tail wagging as he hopped from one slab of road to another.



I pulled open the door with shattered glass panes that led to the other set of stairs, letting Bitch and the dogs through.  As she passed me, Bitch murmured, ``You're angry.''



``Yeah,'' I admitted, ``Bunch of stuff earlier this afternoon.  Didn't go the way I wanted.  Assholes.''



``Should hit 'em.  Teach them to fuck with you.''



``I did,'' I answered, ``Knocked one of them on her ass last night.  Part of the reason things didn't go so hot, today.''



``Mmm.  Story of my life.''



We headed up the stairs and towards the lighthouse.  My bugs were starting to accumulate.  Our detour had given the flying bugs time to catch up to me.  Wasps, moths, houseflies, no-see-ums, a few bees and a fair few cockroaches.



I'd learned my lesson on our last outing.  I wasn't going in unprepared and unarmed.  As they arrived, I drew the bugs close.  Selecting the best of them, I directed them under my armor – in the hollow space beneath my shoulderpads, under my belt, my elbows and wristguards, in my hair and the concave panel of armor that covered my spine.  They were there if I needed them.  I doubted anyone would notice unless I let them.



``How'd you know I was angry?'' I asked.



``Dunno.  Looked that way.''



``Yeah, but you can't see my face.''



``Way you're standing, I guess.  You going to get on my case about this?''



``No.  Sorry,'' I answered.



I decided to keep quiet for the rest of our trip to the `lighthouse'.  Interestingly, she almost seemed to relax as the silence lingered.  Her face lost that slightly angry expression and she reached over to scratch Brutus on the side of his neck in what seemed a very normal, casual gesture, for someone I viewed as anything but.  Or at least, it would have been normal and casual if the dogs weren't currently the size of small ponies.



We reached the lighthouse, and sure enough, there was a group of villains waiting.



Kaiser was first and foremost among them.  He was decked out head to toe in elaborate, ornate armor with a crown of blades, but the configuration, I noticed with interest, was totally different than it had been just two days ago.  Fenja and Menja stood at either side of him.



Only one of the Travelers was accompanying our group: The girl with the sun design on her costume, red suns on black form-fitting armor.  Just behind her were two members of Faultline's crew. Newter was hanging off the wall by his fingertips and toes, and Labyrinth was leaning against the same wall, just below him, her arms folded.  Newter was wearing tattered jeans and had dyed his hair a cobalt blue, setting off the orange of his skin.  He had cloth wrap, like you'd see a kickboxer use, wrapped around his hands and feet.



Rounding out our group were two men in matching kevlar armor, with balaclavas, visors, and tricked out assault rifles.  Each of the men had a second gun slung over their back – I thought one was another rifle, but I didn't have a good view of the other.  I might have pegged it a grenade launcher.  Coil's men, probably.



Fenja or Menja – I wasn't sure which – leaned over and whispered in Kaiser's ear.



``Arrived with less than a minute to spare, Undersiders,'' he purred.  ``Watches out, everyone.''



I paused – I hadn't brought one.  Then I remembered the cell phone.  I retrieved it from the compartment, the cluster of bugs I had in there moving automatically out of the way of my hands.  If anything, they made it easier to know where my fingers should reach to grab it.



``Set time to four-forty in three, two, one\ldots set.  The attack is scheduled to start in five minutes.  We'll use the time to get there, get in position and decide our method of attack.''



Nobody argued.



``Move out,'' he directed us.



Bitch turned her attention to Brutus, who made a groaning noise as he suddenly swelled.  Splits appeared in his skin as he grew another two or three feet taller at the shoulder, and spikes of bone erupted from his exterior.  He stretched, then shook abruptly, spraying all of us with the bloody aftermath of his sudden growth.  There were reactions of alarm and startled shouts from everyone present, with the exception of myself, Bitch and Labyrinth.  Kaiser, surprisingly, was among them, backing away several steps before he realized Brutus wasn't attacking.



There was a bit of swagger in her posture as Bitch walked the two steps to where Brutus stood, grabbed a spike of bone and hauled herself onto his back.



It was intentional, maybe a bit immature, but she'd made Kaiser flinch.  Taking him down a notch like that, so soon after he'd assumed control of this impromptu team, it was probably more of a statement than anyone present could have accomplished with words.



As if to drive the point home, she gave Brutus a light kick in the ribs, prompting him to walk in the direction Kaiser had indicated.  Judas, Angelica and I were right behind her.  I didn't turn to see how long it took the others to pull themselves together and follow.





