





However effective Bitch's power play might have been, it didn't do much to help the tension between the factions making up our group.  It hadn't been just Kaiser that got spooked and sprayed with blood.  Worst case scenario, if a fight broke out in the group, I was worried that hard feelings from that one thing could set others against us.



I decided to try to remedy that.  The Travelers seemed to be the only group present where there wasn't some drama already mucking the waters.



``Hey,'' I slowed my pace so I could talk to the girl from the Travelers, ``What's your name?''



``My codename?''



``Yeah.''



``Sundancer.''



``I'm going by Skitter.  Couldn't decide on a name so the media sort of picked one for me.''



``You're one of the Outsiders, right?''



``Undersiders.  I'm new to the team, honestly, but they're alright.''



``Uh huh.''  She looked in Bitch's direction.



``Not as bad as you'd think,'' I said, smiling.  She couldn't see me smile, with my mask covering my mouth, but I did hope she could hear the humor in my tone.  ``How's life among the Travelers?''



She seemed caught off guard at the question.  It took her a few seconds to decide how to respond.  ``Intense.  Violent.  Lonely.''



The answer surprised me.  She chose the word intense rather than exciting, but that wasn't the strangest part of her answer.  ``Lonely?  I wouldn't think that was the case, spending time with teammates.''



She shrugged, ``There's stuff going on that makes hanging out less fun than it should be.  I'm not going to explain it, so don't ask.''



I raised my hands, palms up, stopping her, ``Wasn't going to.  I was just curious what it's like for other teams, since I'm fairly new to this.''



She relaxed a bit at that.  ``It's not just the\ldots I can't think of a word better than drama\ldots but drama sounds like such an understatement.  Whatever.  It's not the other stuff that's going on, it's that we're constantly moving, rarely spending more than a week in one place, you know?''



``I don't,'' I admitted.  I fudged the truth a little, just to be safe, ``I moved twice as a kid, but I was too young to remember it.  For the most part, I grew up here.''



``It gets old, having to--'' she stopped talking as I was suddenly pushed to one side.  The tip of Newter's tail pressed against the center of my chest and moved me back, pushed me against the hood of a dilapidated old car.



``Hey,'' I grunted, but he shook his head, pressed a finger to his lip.  His blue eyes bored into mine.  They were weird eyes.  No whites, just azure blue irises that extended from corner to corner, with rectangular, horizontal pupils.



I looked at the others, and they were all moving into cover.  Kaiser, Fenja and Menja had all ducked into an alleyway.  Bitch and her dogs were disappearing around the far corner of the same building, making only the scratching noise of claws against concrete.



Ahead of us, a trio of people in ABB colors crossed the street.  A guy and a girl who looked like they might have been gang members before Bakuda's hardcore recruitment drive were talking.  A teen who was about my age trailed behind them, looking too scared and worn out to be anything but one of the new recruits.  They were all armed.  A machete dangled from the male thug's hand, while the girl was toying with a handgun.  The scared looking kid had a baseball bat with nails hammered into it.  People really did that?  The nail-studded baseball bat?



Just behind them was the building that had to be our target.  It was a warehouse, dirty gray, with the letters `ABB' spray painted on and around the loading bay door in red and green in an elaborate style.



When the patrol was gone, Newter spoke, ``They've got patrols, and they've tagged the building.  That'll be our target, today.''  He checked his watch, ``Two minutes until it's time to move.''



``My girls and I will circle around,'' Kaiser stated from the cover of the alleyway, ``Attack from another direction.''



``Hey, no,'' I replied, ``That's not the deal.  We're in groups like this for a reason, and that reason flies out the window if we split up like that.''



``I didn't ask your permission,'' Kaiser replied, his voice cool.  Without waiting for a response, he turned to leave, Fenja and Menja following him.



``Are we going to stop them?'' I asked.



``I could catch up to them,'' Bitch told us, as she rode Brutus back towards our group.



Newter shook his head, thin lips pressed into a line that only accented his strange appearance, ``Not worth it, and dangerous to fight amongst ourselves in enemy territory.  We don't have time, anyways.''



``Bitch, can you call Grue and Tattletale, let them know?'' I asked.  ``They can take measures if they need to.''



She nodded and got her cell phone out.



While Bitch made the call, Newter beckoned the others to gather in a huddle.  ``Let's talk plan of attack.  Skitter, Bitch, you two have the most experience dealing with these guys, so start us off.''



I glanced at Bitch.  She was busy with the call, and she \emph{had} been out of action during our last encounter with the ABB, which left her kind of in the dark as far as Bakuda went.  It was up to me.



I silently cleared my throat, then I spoke up, ``Bakuda likes to set traps, and if this place is important enough to patrol, it's important enough to have some traps.  Let me send my bugs in first.  I can get the lay of the land, and the bugs will also confuse and distract anyone inside, which should make things easier on you guys.''



Newter nodded once, ``Okay.  That's step one.  Bitch, can you and your dogs hit the ground floor?  I'll go in the second floor window.''



Bitch gave him a curt nod in response.



``The bugs won't bite her?'' Newter asked.



``No,'' I answered, ``Won't bite you either.''



``They couldn't if they tried,'' Newter answered me, smiling.  Funny, if you looked past the odd appearance – the blue hair, the weird eyes, the orange skin and the tail, he was actually a pretty good looking guy.



``Sundancer, what can you do?'' Newter asked.



``I guess you could say I'm artillery,'' Sundancer replied, ``But I've got the same problem Ballistic does – er, my other teammate.  I'm not sure I can use my power without hurting a lot of people really badly.''



``Then stay back with Labyrinth.  You two be ready to cover our retreat or move in if we run into trouble,'' Newter replied.



``Sounds like you know what you're doing,'' I commented.



``Maybe some of Faultline has rubbed off on me.''  He smiled.  Then he glanced at his watch, ``Twenty seconds.''



Newter glanced at the two soldiers Coil had sent, ``You two, can you--''



``We're taking a position on this rooftop, here,'' the shorter of the two men replied, pointing up to the two story duplex next to us.  ``We'll support you with cover fire.''



``Uh, good.  Try not to kill anyone,'' Newter said, checking his watch again, ``Five seconds.  Skitter?  Start us off?''



I reached out to all the bugs I'd gathered, minus the ones I was keeping beneath my costume.  I directed them towards the side of the building we were facing.



The swarm swept in through windows that were open or broken and the one open door on the side of the building, flowing into the hallways.  I made sure to spread them out to cover every surface, feeling for anything that was out-of-place or unusual.  There were a fair number of people inside, which wasn't a huge surprise, but my bugs were making a lot of contact with bare skin.  I realized the people gathered in the open area of the warehouse's ground floor were nearly naked.  Stripped down to their underwear.  It was so unexpected that it threw me off my stride.



I shook my head.  I couldn't afford to get distracted.  Bakuda probably used metals and plastics, and to the superfine senses of the bugs, that was an entirely different texture from the walls.  I tried to filter out the usual stuff and get a feel for just the plastic or metal things.  Just a few feet in from the entrance, I found two dome-shaped bulges on either side of the stairwell that led to the second floor, metal and plastic.



``There's something there,'' I said.  ``Give me a second.''



I took a page out of Grue's playbook and gathered a group of bugs together into a densely packed, vaguely humanoid shape.  I moved that collection of bugs through the doors and to the place where the little domes sat.



The explosion blew a fair sized chunk out of the exterior wall of the building closest to us.  The people inside, already nervous at the influx of bugs, started scattering, screaming, running for the exits.



``Holy shit!'' Newter's eyes went wide.



``Motion detectors, I think,'' I said, ``Or proximity activated.  My bugs wouldn't normally set them off, had to fool them.''



The ground was too hard for landmines, so I focused on having the remainder of the bugs sweep through the rest of the building, skimming the surfaces and looking for more trouble.  I found two more, checked nobody was near, and used the same method to detonate them.  The plumes of flame, smoke and debris were visible from where we crouched.



``Twenty or thirty people on the ground floor, unarmed and half naked, ten in upstairs office, armed,'' I said, ``Route is as clear of traps as I can get it.  Go!''



Bitch lunged into action, Newter only a few steps behind.  He half-ran, half-crawled, his tail whipping around behind him, presumably to help keep his balance.



As Bitch had her dogs crash into and through the closed metal loading bay door, Newter intercepted the first few people to leave through the fire exit door on the side of the building.  He leaped to close fifteen foot gaps as fast as I could have thrown a punch, moving from one person to the next, dropping each of them in an instant.  Lots of women in that group, and I could confirm with my eyes what my bugs had told me – nine out of ten of the people in that group, a mix of Asian men and women, were only wearing their underwear.  Slave trafficking?  Prostitution?  Something darker?  I felt my skin crawl.



As he darted up the side of the building and slipped into an open window like a bolt of greased lightning, I felt Newter brush past several with my bugs.  Each bug that came into contact with him dropped off the wall or out of the sky, falling to the ground, alive but stunned.



I remembered reading about him on the web.  Information had been scarce, since Faultline's crew weren't the types of villain to appear in the papers or on TV, and the concrete details that were out there had been hard to pick apart from the speculation.  What I \emph{did} know was that his bodily fluids were potent hallucinogens.  Even the sweat that accumulated on his skin was apparently enough to send someone off to la-la land, taking only a few seconds for it to be absorbed through the skin.



I focused my attention on tracking what was happening inside the building.  Newter was on the second floor, probably dodging gunfire as he moved closer to the group of people who had been in the upstairs office.  I had my bugs cluster around them, biting their hands and faces.  I sent them crawling into noses, ears and mouths to disrupt the aim of the people who might shoot Newter.



Kaiser, Fenja and Menja were attacking from the side of the building opposite us.  They had drawn the attention of most of the armed agents and patrols, leaving Bitch and her dogs stranded in the midst of one or two dozen unarmed, unclothed, panicked people.  From what my bugs were sensing, she was giving lots of commands to her dogs.



I realized, belatedly, that someone had blocked off the route Bitch might have taken to reach the fighting.  The edges of the offending barrier were thin, sharp.  Blades?  That meant Kaiser would be the one who had blocked her.  Was it intentional, or had he been cutting off the ABB's escape routes?



I couldn't sense what Newter was doing since my bugs couldn't touch him, but I could feel the movement of the air that followed in his wake, I could track the locations of the bugs he came into contact with before they were brought down by the drugs, and I knew the men were collapsing as Newter moved into their midst and knocked each of them out with a touch.  One or two even collapsed without him touching them.  Something else?  Blood?  Spit?



Only one remained standing.  He and Newter circled one another.  My bugs weren't having much effect on him, since he was wearing a bandanna or something over his face.



No, wait, there was a second person, just behind Newter.  How had I not noticed him?



Then the first disappeared, and I knew.



I grabbed my phone, accessed the contacts, and auto-dialed Bitch.



``Come on, answer, answer,'' I whispered at the phone.



Then a handful of my bugs were stunned and a few more squashed as Newter collapsed on top of them.  I directed most of the bugs in the building to distract the attacker, hoping to buy Newter enough time to get away.  It wasn't working – he wasn't moving.



``Fuck! Answer, Bitch!''



``What's wrong?'' Sundancer asked.



``Newter's hurt.''



Labyrinth put her hand on my shoulder, half-spun me to face her.  She didn't say a word, her expression barely changed behind the cloth of her mask, but it was still the closest I'd seen to an emotional response from her.



I would have said something, but Bitch chose that same second to pick up.



``Bitch!  Second floor, Newter's wounded, \emph{Oni Lee} is in the building.''



There was a long pause before she replied, ``Lung's here too.''









