





``Lung's there,'' I echoed, as much to let Sundancer and Labyrinth know as to help myself process the idea.



``He's with Kaiser.  I can't get to them.  Kaiser blocked the door with giant knives.''



``Ignore Lung!'' I stressed.  If Kaiser wanted to go it alone, he could reap the consequences.  ``Priorities are Newter and Oni Lee!  Can you get upstairs to rescue Newter?''



``I can't ride Brutus in there, I'd have to dismount.''



``Then draw him outside!  Watch your back!''



I hung up, shoved the phone into the compartment behind my back, and drew my baton and knife.



``What are you doing?'' Sundancer asked.



``Oni Lee's a freaking assassin.  I can't leave Bitch on her own.''



I didn't wait another second.  I bolted for the warehouse, drawing more bugs from the surroundings to help back me up.



Bitch, still riding Brutus, came rushing out the loading bay door, Judas only a step behind.  They skidded to a stop, facing the building.  Through the hole the explosion had made in the wall, I saw Angelica climbing up the stairs.



As Angelica reached the top of the stairs, Judas lunged up and through the windows at the opposite end of the second floor hallway, trapping Oni Lee in between them.



Oni Lee barely seemed to care.  I could see him in his black bodysuit with belts and bandoleers of knives on it, his mask with the demonic face and leering, fanged, ear-to-ear grin.  He glanced at one dog, then the other, then looked out the window.



I knew his power was a hybrid between duplicating himself and teleportation.  He could teleport, but when he did, he left a body behind that could act autonomously for a few seconds.  So when I saw him glance out the window, I followed his line of sight, and saw he had already appeared just behind Bitch, half-crouching on Brutus' back, one hand on a hook of bone to help him balance.  There was a flash of steel in his other hand as he reached around her throat with a blade.



``Bitch!'' I screamed.  It didn't matter.  At the same time as I opened my mouth, a red dot and a mist of red appeared out of the back of his head.  A split second later, another dot and spray of red appeared on his back, around his heart was.  He fell on top of Bitch's shoulder, limp, then collapsed to the ground.



A second later, he exploded into an opaque cloud of white ash, ten feet across.



I glanced over my shoulder, saw the dark silhouettes of Coil's men lying down on the edge of the rooftop.  One had a pair of binoculars, the other was set up behind a long rifle with a prominent scope.  A sniper team.



Anyone else would be dead by now, but the fact that the body had exploded into dust meant it was just a clone, a leftover remaining behind after Oni Lee had teleported away.  He probably wasn't remaining in one place for more than a second.  My bet was that he was appearing, immediately looking for a new target or vantage point, then making a quick exit, leaving the clone to do the deed.



I reached Bitch and cast a nervous glance over my shoulder for Oni Lee. ``You okay?''



``Felt the fucking steel on my throat,'' she rubbed her throat as if she was checking it was okay.  ``Where'd he go?''



I saw Oni Lee for only a fraction of a second, as he fell from the roof of the warehouse, before he exploded into another cloud of white dust.  Another point for the sniper team.  Why had he been up there?  Who or what had he been trying to see?



``The snipers,'' I breathed, whirling around.



Where the sniper team had been, there were four figures now.  I saw the rifle fall from the edge of the roof as the two soldiers struggled with a pair of Oni Lees.  Then, puff, the clones were gone, and there was enough white dust around them that they wouldn't be drawing a bead on him again, even if they hadn't lost the rifle.



But where had he gone from there?  I looked around, feeling the panic begin to set in.



Brutus made a roaring sound somewhere between a howl and a growl, not quite recognizable as either.  He reared like a panicked horse, and I saw Oni Lee drop from the side of his head, land in a crouch, and lunge for me, a knife in each hand.



I swatted at his hands with my baton, sending one knife flying through the air and breaking his stride.  It didn't matter.  Less than a second later, he was dust.  He'd teleported.



Hands seized me from behind, in a rough nelson hold, pulling my arms out of the way as another Oni Lee materialized out of the dust in front of me, ready to capitalize on my inability to defend myself.



Knowing he wasn't about to let go of me, I brought both my legs up in a kick at Oni Lee's stomach.  They connected and he doubled over.



Brutus lunged forward, biting at him before he could recover.  Both the Oni Lee that was holding me and the one clasped in Brutus' jaws turned to carbon ash, adding to the volume of the opaque, gritty white cloud that surrounded us.  As Bitch managed to get Brutus under control I saw his face.  One of his eyes was in ruins, and volumes of blood and other liquids were flowing from it.



``Fuck this,'' I growled, drawing the bugs out from my costume, and retrieving the ones I'd had in the building.  I spread them around, reaching for him, hoping for some sort of early warning.



No sooner the thought crossed my mind than the silhouette of a figure appeared twenty feet to my right.  He whipped his arm in my direction, and I didn't have any time to do much more than turn in his direction before something collided with my head.  I stumbled and fell over backwards.



In the instant I toppled over, I had the presence of mind to tuck my chin against my chest so I wouldn't add to my concussion.  The armor covering my shoulders took the worst of the impact.



As I lay there, trying to parse what had just happened, I realized that a small knife was embedded in the armored section of my mask, cracking the lens.  A throwing knife?  I pulled it free and pulled myself to my feet.  I had enough bugs around me now that I could be sure he wasn't attacking us.  That just raised the question of where he was.



``Bitch, you okay?'' I asked.



``Fucker stabbed me in the arm!''



\emph{If that's the worst injury we get away with today, we can count ourselves lucky.}  I headed out of the cloud that surrounded us, hoping to get a better sense of the battlefield.



I got out just in time to see Oni Lee tackling one of Coil's snipers off the edge of the roof.  Oni Lee disappeared in a cloud of white before he hit the ground.  I was pretty sure the sniper hadn't.



Sundancer was crumpled over, Labyrinth holding her shoulders.



This was not going well.



Oni Lee appeared thirty feet away from me, standing just to my left and behind me.  My bugs gave me a sense of his position before anything else, and I threw myself to one side.  I thought maybe I saw the shape of one of his throwing knives pass through the air where I'd been standing, but I wasn't seeing very well with a cracked lens on my mask.



At my command, The bugs that had alerted me to his position gathered on him and began biting and stinging.



Then I noticed something weird.  More bugs popped into existence in the midst of the cloud, near Sundancer and Labyrinth.  I felt the original bugs perish as they exploded into ash.



He was taking them with him.  I don't think he could help it.



I could track his movements.



``Bitch!  Here!'' I shouted.



She lunged out of the cloud, still astride Brutus, pulling up short to avoid trampling me.



``I can see where he's teleporting,'' I told her, ``Get Judas and Angelica.''



She whistled, long and piercing.  As if in response, Oni Lee appeared just a few feet away.



``Behind you!'' I pointed.



Brutus whipped around, snapping and snarling, and Oni Lee had to backpedal to escape being caught in the mutant's jaws.  He disappeared just a second later.



``Get one dog near those guys,'' I pointed to Sundancer and Labyrinth, ``We should join them asap.''



She nodded, whistled, and pointed.  No sooner did Judas and Angelica arrive at our sides than Judas headed off to his next destination.  Bitch offered me a hand.



I gratefully took it, letting her help me up onto Brutus' back.



As we approached Sundancer and Labyrinth, the sidewalks on either side of us dropped out of existence, leaving only a bottomless pit where they had been.



``The fuck?'' I murmured.



Then the buildings began to rise in height, some leaning over the street and joining with the others in grotesque arches and bridges.  Brickwork stretched and extended into the alleyways, closing them off.



Then windows began to shrink and warp, leaving only flat expanses of brick, concrete and stucco for the building faces.  Under our feet, the road began to shift in color, with some patches becoming paler, and others darkening.  They sharpened in definition as they settled into an alabaster white and jet back.  A checkerboard?



Brutus had to leap out of the way as one of the squares of the checkerboard suddenly rose to a height of ten feet.  As if in response, other squares began to rise and fall, each to varying, almost random heights.



I was almost dismounted as another square appeared in a wall and slid out of the side of the building in a thirty foot long horizontal pillar.



We reached safe haven, an expanse of unaffected ground, thirty feet across, with two figures in the center.  Sundancer and\ldots Labyrinth.



``This is you?'' I asked Labyrinth, awed, as I climbed down off Brutus.



She didn't reply.  Instead, she reached out and touched the side of my chin.



The images of arches, pillars and checkerboard patterns fell away like a house of cards.



``Hallucinations,'' I spoke, as Labyrinth made a waving gesture towards Bitch's head.  She looked at me and shook her head slowly.



``They're not hallucinations?'' I asked.



She didn't reply.



``You can't explain because you can't or don't talk,'' I realized, speaking my thoughts aloud.



Oni Lee appeared a few feet away.  I whirled and pointed, ``There!''



He was stumbling, moving to avoid something that wasn't there.  He was still there, trying to get his balance, as I felt more bugs appear at another point on the opposite side of us.  Only he appeared fifteen feet in the air, fell, and landed in an awkward position, falling over.



``Bitch!'' I pointed.



She whistled and pointed to send Angelica.  Oni Lee's response was delayed, as if he couldn't even see her approaching, at first.  I felt more bugs pop into existence a second before she set her jaws on him.



``There!''



Bitch sent Judas next.  Oni Lee's reaction was even slower, but he had time to throw himself onto his back, flinging two throwing knives into Judas' face and shoulder before he disappeared.



``Over there!'' I pointed as he reappeared.



Bitch didn't even have time to give a command before there was a sound like a champagne cork being popped.  Oni Lee screamed as one of his shins exploded in a spray of blood.



I felt him reappear somewhere else, collapsing to the ground, while his predecessor endured having the kneecap on its good leg shot out.



I followed the sound of a chamber being reloaded to spot Coil's sniper.  He was lying on his side at the foot of the building, one arm outstretched to hold his rifle steady.  His right leg was bent the wrong way.



He'd been knocked off a three story building, had a broken leg at the very least, and had still managed to retrieve, load and fire his rifle?



If he was willing to be that professional, I could damn well play spotter for him.



``There!'' I pointed in Oni Lee's direction.  On the warehouse again.



There were two more muted popping sounds, and I could see Oni Lee spin in a pirouette of sorts as a shot clipped him, before he collapsed to the rooftop.



He exploded in a cloud of ash once again.  Except I hadn't felt him appear anywhere.



``He's gone,'' I said, ``Out of my range.''



Sundancer looked up at me, one gloved hand on her shoulder.  ``Good,'' she managed to answer.



``You okay?''



``He gouged my shoulder.  I'll need stitches, but it's not the worst injury I've had.''



``Okay.  Uh, man, Coil's guy,'' I spoke, trying hard to organize my thoughts and priorities with the adrenaline that was pumping through me, ``You going to be alright?''



``Yeah,'' he rasped, then he coughed.



I'd have to take him at his word.



``Labyrinth, watch him.  Make sure he keeps breathing and that his buddy knows where he is,'' I said, ``Sundancer, Bitch, we've gotta go help Newter.''





