





I didn't like leaving Labyrinth behind, after seeing her help turn the tide of our fight against Oni Lee, but I couldn't use someone that couldn't communicate with me.



Bitch, Sundancer and I all sat astride Brutus as he headed towards the warehouse once again.  My bugs lagged behind us.



``We should be fighting Lung,'' Bitch growled, ``Not helping the freak.''



``What?'' Sundancer asked, ``Why wouldn't we help him?''



``His fault if he got hurt,'' Bitch snarled.



``And if you got hurt?'' Sundancer challenged her, ``You'd want us to leave you?''



``Fuck no.  But I wouldn't be surprised if you did.''



``We're helping him,'' I stated, firm.



``Yeah?  I'm the one telling this big lug where to go.''  She slapped her hand on the side of Brutus' neck a few times.



I would have yelled at her, should have, maybe.  Instead, I just leaned forward until I was pressing against her back, and spoke into her ear, ``We let him die, you think Faultline's going to let it slide?  She might hurt or kill Tattletale or Regent in retaliation.''



My piece said, I leaned back and waited to see how she'd respond.  If that wasn't enough to convince her, and I had no idea if it would be, I was ready to try jumping off Brutus' back and seeing what I could do to help Newter on my own.



Bitch didn't reply.  She didn't take us around, over or through the building, either, though.  When we stopped, it was by the stairwell leading up to where Newter had fallen.



The business they had been into wasn't prostitution or slave trading.  Long tables were arranged around the ground floor of the warehouse, with stools lined up beside them.  On those tables were shallow boxes with blocks and piles of a white powder.  Various tools – rulers, funnels, scales, measuring cups and no-name brand boxes of sealable plastic bags were arranged around each station.  Heroin?  Cocaine?  I didn't know my drugs well enough to guess.  The center of the room had been left more or less clear, maybe so cars or trucks could pull in.



So the 'employees' had been wearing little to no clothing, presumably, to keep the clothes clean of the white dust.  Or maybe to keep them from pocketing any drugs for themselves.



The building rumbled with an impact, and I was reminded of the business at hand.  Was I more distracted than usual, right now?  Was it the concussion?



Bitch had been right, before – the stairwell and what I could see of the the second floor was too low for both a dog and a rider.  I hopped off Brutus' back, stumbling a bit as I landed, then headed up the stairs, taking them two at a time.



Newter was lying in a puddle of blood, in the midst of a bunch of thugs, who were all lying down, crawling or writhing, oblivious to my existence.



Seeing the thugs was enough to remind me of how dangerous it would be to touch Newter.  I was wearing gloves and leggings with padded soles, but would that be enough?  The dragline silk I'd used for my costume was \emph{mostly} waterproof, but the weave itself was porous, and I was worried enough that touching his blood could mean a terminal overdose that I couldn't risk it.



My approach stopped short of the puddle.  Newter had a knife wound just below his shoulderblade that traced around his side, as long as my forearm and deep enough that I couldn't tell how bad the damage was.  He was breathing, but his breaths were shallow enough that I almost couldn't tell.  I was here, I could bend down to touch him, but I was helpless to do anything.  Moments after I made contact with his skin, even with my gloves on, and I'd probably be on some hallucinogenic drug trip, flopping around like a fish on dry land.



Bitch and Sundancer approached from behind me, stopping at my side.



``Bitch, go downstairs, check the supplies they were using with the drugs.  Look for rubber gloves, saran wrap, anything like that.  If you can't find anything, look in the bathroom, under the sinks.  I doubt there'll be a first aid kit, but if you can find one, bring it.''



Bitch didn't answer, but she headed down the stairs.  Just to be safe, as my bugs reached the building, I swept the flying ones through the rooms to help me look for first aid supplies and to keep an eye on Bitch and the rest of the building.



``What are \emph{we} doing?'' Sundancer asked.



``You're staying with him.  See if you can get a response, talk to him.  I'm checking in there.''  I pointed to the office at the end of the hall.  Just in front of the door there was a gaping hole in the wall and a pile of debris – the mess Judas had made when he'd lunged through the side of the building to corner Oni Lee.



I had a dim recollection of what my bugs had sensed when they'd first entered the building and checked out the room.  I'd been more focused on the people and potential booby traps, but I remembered that it had been an office, with a desk and a curtained off area with a bed.  Maybe the bed was there so the guys in charge could take turns sleeping there, ensuring there was always someone to keep an eye on things.  Maybe it was for the half-dressed 'employees', for taking advantage of them or so there was a place to put the ones that accidentally overdosed while working.



Entering the office, I confirmed my suspicions about the existence of the bed.  I began stripping the badly stained sheets off.



Was it odd that this place freaked me out ten times as much as nearly getting offed by Oni Lee?  Drugs had always spooked the hell out of me.  One of the first times I'd ever ridden a bus, when I was around five or six, I'd seen a methhead freak out, making enough of a ruckus that the driver had to stop and force him off.  I'd never really gotten over that first impression, where just the idea of being around someone that was high made me sort of anxious.



It wasn't just that, either.  In grade school and junior high, I'd had classmates drop off the face of the planet, hearing only rumors and hints from other classmates or my teachers that there were drugs involved.  Either my classmates themselves getting caught up in things, or parents or siblings dragging the kid into their mess to the point that the kid couldn't come to school.  One as bad as the other.  Almost from the beginning, I'd had this sense of drugs as this unstoppable black hole of fucked-up-ness that swallowed in anyone close to the addict.



Yet people did it.  It was something common and profitable enough that in an area like Brockton Bay where there were as many people unemployed as not, the ABB needed a money counting machine in this very office.  Profitable enough that they had an open safe with stacks of bills inside.



My bugs weren't doing much, so I set them the task of collecting the money.  Within a second or two of my having the thought, the mass of roaches, centipedes, pillbugs and ants flowed into the piles of money and began pushing it all off the desk or into paper bags.  Houseflies and wasps gathered on the bills that tried to fly through the air and retrieved them.  It wasn't perfect, it was a little clumsy, but it still caught me off guard just how well they were able to coordinate for something like that, without any conscious direction on my part.



I couldn't let myself get distracted.  I could put my bugs on autopilot and have them finish the job while I focused on more important things.  Pulling off the bedsheets, I uncovered a plastic sheet.  The kind you used when your kids wet the bed.  Doped out drug addicts, too, maybe.  The top of the plastic sheet looked kinda grody, but I wasn't in a position to be picky.  I pulled it off the mattress, balled it up in my hands and hurried back into the hall.



``Help me,'' I ordered Sundancer.  With her help, I laid out the plastic sheet, bottom side up, at Newter's feet.  By the time we had it flat and ready, Bitch was returning.



``Found two pairs of plastic gloves and some rubber gloves under a sink,'' she said, ``First aid kit, too, but it feels light.''



``Open it,'' I said, taking a pair of plastic gloves.  It was awkward, fitting them over my normal gloves, but I managed it.  Sundancer just pulled off her costume gloves and put on the plastic ones.  She was caucasian, I noted, pale.  ``Tell me what's inside, fast.''



``Got some tape, bandages, thermometer, safety pins, rubbing alcohol, soap\ldots''



``Needle, thread?'' I asked.



``No.''



``Gauze pads?  Big bandages?''



``No.''



With our plastic gloves on, Sundancer and I managed to haul Newter onto the plastic sheet.  The moment she let go, Sundancer winced and reached up to her shoulder, but she stopped short of actually touching it.



I turned to my teammate, ``Bitch, go downstairs.  Those people who were in here took their clothes off and my bugs say they stashed the clothes in a room below us.  Find me some purses, as many as you can grab, as fast as you can grab them.''



She didn't move, this time.  She just glared at me.



``Fucking move!'' I shouted at her.  She gave me the evil eye before she left again.



``Bandages are going to be too small,'' Sundancer said, as I tried to wrestle Newter's blood-slick tail onto the plastic sheet.



``Douse them in the alcohol, use them to clean the injury of blood.  Use the dry bandages to pat it dry so the tape can stick.  Don't be afraid to get into the wound, just be gentle.''



She nodded, and began working on it.  I grabbed the tape and began fumbling with it.  Two pairs of gloves on, and I couldn't lift off the end of it.  I grabbed my knife and used the edge it to get the job done.  Once I had the tape, I began holding the wound closed and taping crosswise across it.



I could only hope I was doing the right things, here.  A month of weekend first aid classes had \emph{not} prepared me for this.



Bitch arrived with purses and practically threw them at me.  I could have gotten pissed, but Newter couldn't afford for me to.  I began emptying the purses onto the ground beside me and sorting through the contents.  Pens, wallets, headphones, books, tampons, pictures, receipts, more receipts, change, keys, yet more receipts\ldots



``What are you looking for?'' Sundancer asked.



The third purse turned up what I needed.  Sanitary pads.  I tore one open and pressed it to the wound, then began taping it down.  Unasked for, Sundancer grabbed another and opened it so it would be ready for me.



``Sterile, absorbent, covers more area than the bandage can,'' I got around to answering her question.  ``If he lives, his teammates might give him a hard time, but it's better than nothing.''



``You didn't tape it down all the way,'' Sundancer pointed out.



``Only three sides,'' I agreed, ``So it can breathe.''  I only vaguely recalled some instruction on that front.  I was hoping it was right.



If I failed \emph{here}, what right did I have to call myself an aspiring hero?



When the wound was bandaged as much as I could manage, the three of us bundled him up in the sheet and lifted him.  Bitch and Sundancer had an injured arm and shoulder, respectively, so they both took his head and shoulders while I took his feet  With agonizing slowness, we carried him down the stairs.  then as carefully as we could manage with a body weighing half again as much as any of us, we draped him across Brutus' shoulders.



A bone-jarring crash nearly undid all of our hard work.  Brutus nearly lost his footing at the impact, and I know I would've fallen if I hadn't already been holding onto him.



A gauntleted hand as wide across as my armspan had crashed through the wall.  The whole building shuddered as another hand punched through the brick of the wall twenty feet from the first hole.  Fingers gripped the building, and pulled the entire section of wall out in one piece.



``Go!'' I shouted at Bitch, ``Take him to the others!  Call Tattetale, get the number for that cape doctor, get medical attention for anyone who needs it!''



She hesitated, opened her mouth to protest.



I raised my voice, ``Do not fuck with me here!''



There was a rumble outside as the removed section of wall was thrown against the ground outside, hard.



Just an instant later, a half dozen ABB members retreated into the warehouse through the hole, taking cover from the giantesses.  They saw us and stopped short, wary, weapons ready but not raised or pointed at us.



Lung followed his thugs into the room.  He was bigger than I'd seen him yet at nearly fifteen feet in height, and was covered in layers of scales that left him barely recognizable as human.  Spearlike growths stuck out of his shoulders in what I realized were the beginnings of wings.  His mask had been torn off at some point, and the features of his face had been warped by his transformation.  The shape of his skull and face were more catlike than human, and his nose and mouth were a single X-shaped opening, bristling with pointed teeth that stuck in every direction.



I could see why he usually wore the mask.



``Bitch,'' I murmured, ``If you don't leave now, I don't think you're going to get another chance.''



``But--''



``Which do you want more?  To fight, here and now, or to make sure Faultline and the other groups don't have an excuse to do anything to our teammates?''



I saw her hesitate.  The fact that she even had to think about it\ldots I could have slapped her.



Kaiser strolled in, unworried, unhurried.  Lung moved like he was going to lunge for him, then stopped just in time to avoid impaling himself on the narrow blade of steel that had erupted from the ground, pointed at his heart.  I wasn't sure if it would have penetrated his covering of scales, but if I were Lung, I don't think I would have gambled on it either.



Fenja and Menja reduced their size to fit through the hole they'd made in the wall, then grew again as they had the headroom.  They settled at a height of eighteen or twenty feet.  Fenja carried a sword and round shield, while Menja had a spear.  Or the other way around, whatever.



In the corner of my eye, I saw Bitch hop onto Brutus, then ride in the direction of the sniper team and Labyrinth, a wrapped-up Newter lying limp in front of her.  Judas and Angelica remained behind, not far from Sundancer and I.  Their entire bodies were taut with tension, their heads low, as they glared at the new arrivals.



Lung turned to survey the room.  His men were arranged in a loose circle around him, facing us.  His eyes settled on me.



``Ooo,'' he rumbled, his words were distorted by the shape of his altered mouth, but it was easy enough to guess what he'd just said.  \emph{You}.





