





``Yeah, me,'' I answered Lung, hoping I sounded more confident than I felt.



``Some history?'' Sundancer murmured.



``I made his crotch rot off.''



She turned to stare at me.



``Accidentally.''



``How do you-'' she started, then she stopped as Lung's growl rose in volume enough to turn her head.



Angelica and Judas advanced steadily until they were on either side of me.



``Step down, Undersider,'' Kaiser spoke from the opposite end of the room, ``My girls and I have this in hand.''



``Do you?'' I challenged him, not breaking eye contact with Lung, ``Because Lung looks like he's in pretty good shape there.  You know how this works, right?  He only gets stronger the longer you fight him.  If you haven't finished him off by now, you're probably not going to.''



Lung chuckled, low and gravelly.  He craned his neck to look at Kaiser, and I shivered.  His neck alone was nearly as long as my torso and thicker at the base, tapering down to a more or less normal sized head.  What was creepier was that he'd bent his neck in a `u' shape to look behind himself.  It was a movement that a gymnast would have been hard pressed to perform with their \emph{back}.  It wouldn't be long before he just wasn't recognizable as something who had once been human.



The six of his thugs that were gathered around him looked like they were almost as scared of him as they were of us.



``What would you propose, then?'' Kaiser asked me.



``Sundancer and I will help out,'' I told him.  I glanced at Sundancer, and she nodded.



Lung laughed again.  ``Ooo?  Ug gurr?''



Before I could figure out what he'd just said to me, he lunged straight at me, passing between two of his people, moving on all fours.



I'd sent the flying insects and wasps into the room to help Bitch search for supplies, and I directed them straight for Lung as soon as I realized what he was doing.  Too little, too late.



Then Judas intercepted him.  The pair of them rolled and tumbled, and I couldn't tell which of them was making which snarling or growling noise.



When the momentum of Judas' pounce had stopped carrying them across the floor, Lung managed to get his footing first, and physically \emph{heaved} Judas across the main floor of the warehouse.  Judas slammed into two sets of the long tables, sending clouds of white powder billowing around him.



When Angelica made her move, Lung was ready for her.  He caught hold of her snout and foreclaw before she could do any damage and leveraged her forward momentum to throw her too, straight at Judas.  There was an almost judo or akido kind of style to the throw, except I doubted either of them were human enough for normal moves and techniques to apply.  What was more likely, I thought, that his reflexes, flexibility and strength were on a level where that sort of thing came naturally to him.



In any case, my bodyguards, if you could call them that, had been tossed aside away like they were stuffed animals.  Lung didn't drop to all fours again as he advanced toward me.  Instead, he flexed his right hand, and my eyes were drawn to the foot-long blades that tipped each finger.



``Sundancer?'' I asked, quiet, ``Help me out?''



``If I used my power, I'd probably hurt you worse than I hurt him.''



``That line is getting old fast.''



Lung lunged again, and I threw myself to one side, too slow, too short a distance.



With the sound of swords being drawn out of their sheaths, a barrier of blades and spears rose up from the ground between Lung and I.  I found traction on the asphalt with my hands and feet, and I managed to half-crawl, half run away from him.



Lung started to move around the barrier of blades, only to be blocked by another bristling growth.  He roared, then leapt for the rafters up at the ceiling.  I knew what he was doing almost right away, and ran for cover – once he had a grip up there, it would be a matter of using his grip on the steel girders that lined the ceiling to jump straight at me.  I wasn't two paces before I knew there was no cover I could get to fast enough.



Except he didn't get that far.  A square pillar of steel  as tall and long as an eighteen wheeler speared downward from the roof, straight at him.  It caught Lung in his midsection and shoved him down into the ground, hard.  A few seconds later, the weight of the block of steel tore it from the section of ceiling it was rooted in.  It didn't hit anyone as it dropped down but I could guess it would've killed someone: I could feel the impact of it striking the ground in my bones.



I looked at Kaiser.  He was standing where he'd been when he walked into the room, hands clasped behind his back.



``Fenja, Menja,'' Kaiser's order wasn't shouted, but it could be heard across the warehouse.  If you could call it an order.



But the two eighteen-foot tall valkyries seemed to know what he wanted.  They advanced towards Lung with their weapons drawn, and Lung's people began backing slowly away.  I felt a pang of sympathy for Lung's rank and file, mainly for the ones who'd been coerced into this.  They'd probably seen what Fenja and Menja were capable of, earlier, but they couldn't run without risking their boss' wrath.  Caught between a rock and a hard place.



Lung wasn't quite down and out yet, though.  He started climbing to his feet, only to have a pyramid of criss-crossing blades spear up around him.  Blades appeared under and over his arms, just beneath his armpit, behind his knee, by his groin, with dozens more rising above and around him. Before he could find his way out, he was trapped.  Buried and hidden beneath the layers of steel.



Kaiser inclined his chin, looking toward the ceiling, and I saw a shimmer.  The tip of a blade began to emerge from one of the iron girders above, revealing itself at a glacial pace.  It was no more than a half foot thick, but nearly twenty feet wide.  I wasn't sure if it was an optical illusion from the rippling energies of Kaiser's power or not, but I thought maybe the ceiling was sagging under the weight of it.  If he wasn't careful, he'd bring the roof down on our heads.



Then Kaiser lowered his head to face the area where Lung was trapped and the massive sword he'd manifested in the ceiling plunged down into the pyramid in a heartbeat.  Sparks showered as the gargantuan blade sheared through the trap.



But there was more hot metal that wasn't a result of the impact.  When I looked again, I saw Lung had avoided the blade.  The side of the pyramid closest to me glowed a white-orange, the blades curling and sagging in the intensity of the heat.  He'd softened the metal enough with his pyrokinesis that he could use his monstrous strength and push his way free.  Enough, at least, to avoid being divided in two.



Lung roared as he climbed free.  As Kaiser raised more blades around him, Lung swung his claws and shattered the metal, sending the pieces sliding across the floor.



``Aiiihurrr,'' Lung growled.



``You're an animal, Lung,'' Kaiser answered him, ``Even without your power making you into\ldots this.  Go down!''  As if to punctuate his statement, a spear of solid steel erupted from the wall and slammed into Lung, carrying him to the end of the room opposite where Judas and Angelica were.  Lung managed to grip the spear and move himself so the spearpoint wasn't pressed against his chest when it punctured the concrete of the wall.



``Your people\ldots animals.''  Kaiser intoned.



Not six paces away from me, one of Lung's thugs let out a raw scream and collapsed to the ground.  Dagger-like blades had pierced the tops of his feet mid-stride.  As he used his hands to break his fall, another set of blades punched through his palms.  The screams of the other thugs echoed his.  He was on his hands and knees, unable to move with his hands and feet effectively nailed to the ground.



``Kaiser!'' I shouted, ``No!''



``Not your business, little girl,'' Kaiser told me, turning in my direction.



I took an immediate step back, fearing blades would appear under \emph{my} feet.



``This is wrong,'' I said, as I watched a sliver of steel sprout out of the ground and rise with a controlled speed to the base of the thug's throat.  He was forced to arch his back and raise his head to the absolute limits to avoid getting a very unnecessary tracheotomy.  I glanced at Lung.  He was watching what was happening, but I couldn't read his alien expression.



``Wrong?'' Kaiser chuckled, ``As far as I'm concerned, the moment you need to fall back on \emph{morals }to argue something, you've already lost the argument.  This is \emph{war}.''



Lung moved for Kaiser, this time.  He virtually rolled to one side to avoid an outcropping of spearpoints angled in a way that he might have run himself through on them, then resumed his charge.



One of the giantess twins stepped in, kicking Lung into and almost through a wall.  Lung bounced back almost immediately, drawing on his pyrokinesis to direct a column of blue-yellow flame at her.  The other twin intercepted the fire with her shield.



A few seconds later, she was stumbling back and away from Lung and throw her shield away to avoid having the heated metal burn her arm.



Kaiser's team wasn't going to win this on their own.  As much as I despised stepping in and helping him\ldots



``Sundancer, now would be a great time to use your power.''  I spoke.  As I said the words, I called on every bug that was in the area and sent them to Lung.



``It's not- no.  I'll burn them.''



``Then burn them!  If you don't use your power, I can pretty much guarantee Lung will burn them worse.''



``Doubt it,'' Sundancer replied.  But she raised her hands in front of her, and there was a brilliant flare of light, only a fraction of a second, but enough to leave a black-blue spot in the center of my vision.  There was a brief roaring sound as the light faded.



I turned my focus to my bugs as another flicker of light appeared, longer and stronger than the first, again, accompanied by that faint roar.



``Hey, Skitter, was it?'' Sundancer spoke.



``Yeah,'' I said.



``Get back.  Way back.''



I ran for it, pulling my mask up and bringing my fingers to my mouth in the best whistle I could manage.



Two seconds later, Angelica shoved her snout between my legs.  Had it been a movie, or if I'd been Bitch, maybe, I would've been able to slide or jump back and land on her neck or shoulders, ride on from there.  As it was, I half-fell, half-rolled over the top of her head and only barely managed to get a grip on a spike on her shoulder.  I clung to that as she ran, praying I wouldn't fall and get trampled.



``Angelica, stop, stay!'' I called out, hoping she knew the command, that she'd listen.  She did, slowing her pace to a walk, then stopping just by the loading bay door we'd come in.  Judas caught up and walked around her, until he was just in front of us.  He was still covered in the white dust, but it didn't seem to be having any real effect on him.  I hopped down from Angelica's side, ready to climb on her and jostle her into action if Lung made another attempt to come after me.  I wasn't sure I could steer her, but with the prospect of Lung chasing me, I'd rather be moving totally uncontrolled at Angelica's speed than anything my own two feet could offer.



Sundancer had managed to get her power going.  A ball of light, larger than a basketball, smaller than a beachball, sat between her hands.



\emph{Light}?  That was it?



Then I saw the floor.



The warehouse had clearly been raised above a flat expanse of asphalt, maybe an old parking lot, and the surface had cracked and been patched a fair bit over the years.  It still bore the oil stains from the old days.



Directly below Sundancer, the floor was normal.  Starting around five feet from her, though, the ground looked wet, glassy.



The asphalt was melting.



She dropped her hands, and the ball of light rose.  Like it had a mind of its own, it darted towards Lung, zipping left and right and up and down as it moved.  I saw how it rose higher as it moved over Lung's people, who were still nailed to the floor.  At one point, it moved only ten or so feet over one of the tables, and the plastic surface of the table seemed to crumple up in fast motion, turning black and smouldering with tongues of flame.



I scattered my swarm, all too aware they weren't doing a thing to Lung, knowing they'd just die when Sundancer got her orb to Lung.



She didn't make it touch him, but seeing what it had done to the table, I thought maybe that was a good thing.  Lung raised a hand towards the light and I could see the heat shimmers in the air.  She pushed it a little closer to him, and his legs buckled.



Kaiser was apparently unwilling to let Sundancer steal the show, because he brought a shaft of metal out of the wall behind Lung, shoving Lung toward the orb.  Sundancer moved the ball back, but just the second or so of close proximity to the ball was enough to take the fight out of Lung.  He fell to all fours, tried to move, and found the asphalt like a molten tar beneath him.



Wasn't he supposed to be fireproof?  Or was that immunity only to the flames he made with his own power?  Or, I thought, was that ball of light -Sundancer's miniature sun- \emph{that }hot?



I was lingering at the exit, watching and waiting to see the outcome.  My bugs were prepared and ready, lingering as close as they could get without being wiped out by the superheated air.



Even with his superhuman constitution, even with his pyrokinesis to maybe take the edge off the effect, Lung was clearly suffering.  Just a matter of time, I realized, before he collapsed.  Probably, I supposed, much longer than one would think, with his regeneration.



Then the light of Sundancer's orb winked out.



It took me a few long moments of blinking the spots out of my eyes before I could make out the scene in its entirety.



Lung was limp, his arms dangling at his sides.  He was still bent over, and he might have fallen face first into the tar, if it wasn't for the spear of iron that was impaling him through the heart.



``What did you do!?'' Sundancer shouted.



``Obviously,'' Kaiser said, ``I ended it.''



``It was already over!''



I was under the impression very few people really argued with Kaiser.  Fenja and Menja joined him, one on either side of him, and neither of them were sheathing their weapons or shrinking back to a normal size.  I took that to be a very bad sign.



I was so preoccupied with watching Kaiser that I almost missed what happened next.



It started as a flash of crimson in the corner of my eye.  I looked, and I saw Lung's wings fully unfurled.  Like the wings of a bat, only they had silvery scales where the bat had fur, and the flesh that stretched between the `fingers' of the wings was the deep, dark red of blood.



Lung grabbed the spear that impaled his chest and snapped it with his claws.  He stood, and his entire midsection seemed to arrange so he stood another foot or two taller.  Taking hold of the fragment that was still embedded in his chest, he slowly slid it out.  Once it free, he cast it aside.  It clattered to the floor of the warehouse.



We were so quiet, you could hear the ringing of the steel as it settled on the ground.



``Sundancer!  Run!'' I shouted, breaking the stillness.  I sent my bugs swarming to Lung.  Anything to block his vision, distract him for even a second.



The events that followed seemed to happen in slow motion.  Lung repeated what he'd been trying to do as the fight opened, only nothing seemed capable of getting in his way, now.  He was faster, stronger, more maneuverable.



He lunged toward Kaiser, using his wings to carry him effortlessly above a growth of steel blades.  Reaching Kaiser, he slammed the man into the wall.  Kaiser went limp, but Lung repeated the process, banging him against the brick of the warehouse wall a half dozen times in the span of seconds.  When he was done, he flung Kaiser away like a toy.



Fenja had to drop her spear to catch Kaiser in her arms, which seemed to be exactly what Lung wanted.  Lung did the same `I explode' trick he'd done to wipe out my bugs in my first encounter with him, only it was ten times the explosion, ten times as big.  The two giantesses staggered back, which gave Lung the opportunity to dart across the floor and drive his flattened, clawed hand into Menja's belly like a knife.



As he withdrew his claw, she collapsed.



``Nessa!'' Fenja screamed.



Lung ignored her and started walking towards Sundancer and I.  Fenja rushed to her sister's side, still carrying Kaiser.



Sundancer began forming her miniature sun once more, with increasingly frequent flickers of light and fire gathering between her hands.



``No.'' Lung boomed.  He raised his bloody claw, and the flame in Sundancer's hands dissipated, slipping out of her grasp like greased eels.



She tried once more, and again, he thwarted her with an almost casual ease.



Before she could make a third attempt, Lung blasted her with a torrent of roaring flame.  For two, three, four seconds, the fire washed over her, consumed her.



When he stopped, there were tongues of flame dancing on the asphalt around her, even her costume had fire lingering on it, but both she and her costume were untouched.



She, at least, was fireproof.  Or she'd had to be, to avoid being burned by her own power.



She wasn't, however, invincible.  As the flames of his attack dissipated, Lung was made visible again, revealed to be standing right in front of her.  He barely seemed to care she was there as he backhanded her aside.



Then he turned his attention to me.



Just me left, really.  I swallowed hard, drew my very underwhelming knife and stood straight, facing Lung.  \emph{Please don't burn me, please, please.  Look at this knife and see it as an insult.  An exc}use to trounce me physically\emph{.}



Angelica started snarling at Lung.  She took a step toward him.



``No!'' I ordered her, ``Back!''



The snarls ceased, and she looked at me.



``Back,'' I repeated.  When I took a step toward Lung, she didn't follow.  A powder-covered Judas stood fifteen feet away, tense, but not approaching either.  Good.  No use in anyone else getting hurt.  There was nothing else she could do.



Hell, I was almost positive there was nothing else \emph{I }could do.



My bugs gathered on Lung, but as far as I could tell, there was no skin, anymore.  No flesh to bite, nothing to sting.



Lung rumbled with a rough, guttural chuckle, and let a brief flame wash over him, wiping the swarm out of existence.



I dispersed the bugs in his vicinity that hadn't yet had a chance to touch him and get burned for their trouble.  No point.  Detrimental, almost.



Then Bitch, riding Brutus, bounded down from the hole in the ceiling and crashed into Lung.



``Bitch!'' I shouted, too late, ``No!''



Once he got over the shock of the initial impact, Lung used one hand to grab Bitch from where she sat on Brutus' back, and took hold of Brutus by the neck with his other.  Heaving his arm, and Brutus, to his left side, then to his right, Lung casting the dog head over heels through the air.



Judas and Angelica began to move forward, but stopped when Lung elicited a scream of pain from Bitch.



``Nnno,'' Lung rumbled.



``Stop!'' I shouted, stepping forward again, ``I'm the one you want, aren't I?''



It always sounded so good when you heard it in the movies.  As I realized what I'd just said, it only sounded stupid.



He advanced toward me, carrying Bitch like a careless seven year old might carry a cat.  I backed away, but his stride was long enough for him to close the gap effortlessly.  He grabbed me and hefted me into the air, lifting me above his head so he could look up at me.



``Ug hurrrrr.''



He couldn't talk, so I couldn't even fall back on the tired old cliche of getting him to monologue.  Fuck.



He had my neck encircled with thumb and forefinger, two claws at my ribcage and his `pinky' finger at my midsection, just below my waist.  He squeezed a fraction tighter, and I groaned.  The fabric of my costume was preventing the edges of his claws from cutting into me, but it wasn't reinforced to stop me from being crushed.



I directed a bug into his eye.  It stayed there, wings fluttering in staccato.  It was annoying enough for him to drop Bitch and deal with it.  He didn't give her a chance to escape, though.  Before he dealt with the bug, he shoved her against the ground and stepped on her, holding her down with his clawed foot.  That done, he used the points of his claw to pick the bug from his eye socket.



He chuckled again, low, gravelly, as he examined the cockroach impaled on his clawtip.  ``Auuhh-roagh?''  \emph{Cockroach?}



He lowered his arm so I was at his eye level.  Then he squeezed again, weaker than the first time.  Shook me, not as hard as he could have.



Then his arm sagged again, until my toes were brushing the ground.  After shaking me, his grip had loosened, and he hadn't really tightened it, so I managed to get my knee against the base of his palm and shove myself backward, push myself free.  My feet touched asphalt, and I backed up a few steps.



``Hurrrrrrrr,'' he rumbled.



``Don't fucking underestimate me,'' I snarled in response.



I don't know if he heard me.  I hadn't even finished the sentence before I had to skip backward two steps to avoid being crushed beneath him as he collapsed face first to the asphalt.



``Bitch, you okay?'' I asked.



She was picking herself off the ground.  She nodded.



``What happened?'' she asked.



I sheathed my knife and reached for my cell phone with one hand.  My other hand, I extended with the palm up.  A cockroach settled on it.



``Wasn't sure it would work, or if it'd be enough.  Took a bit of caterpillar, had a roach swab it in that pool of blood Newter left upstairs, and mashed the thing in Lung's eye.  Big and tough as he is, a drug that strong in the mucus membranes of the eye?  So close to the brain?  Apparently it's enough.''



Bitch folded her arms, looking down at Lung.  Then she looked up at me.



``Now what?''



It was a surprisingly apt question, coming from her.  Did we just leave him here?  He'd be all better in a matter of minutes.  There were options.  I just didn't like any of them.



I dialed Tattletale's phone, but it was Regent who answered.



``Hey,'' he said.



``A, lemon,'' I said.



``C, grass,'' he replied, ``You wouldn't believe it.  We found one of Bakuda's workshops.  The stuff she has here is crazy.''



``No time to chat.  I need to talk to Tattletale, fast.''



``She's checking the place for booby traps.  Distractions probably aren't a good idea.''



``It's kind of important,'' I said, looking down at Lung.



``Right.''



Two seconds later, Tattletale's voice was on the other end, ``Hey?''



``Quick question.  I have to be sure, which is why I'm calling you.  Lung heals, right?''



``Yeah.  Wait\ldots Lung's there?''



``Unconscious at my feet.  But I don't know how long, so answer fast.  He heals?  He's already healing what I did to him from last time, right?''



``Right.  He'll heal pretty much anything, given time, provided he isn't dead.  Lose an arm, he'd grow it back in a few months.''



``Thanks.  That's what I needed to know,''  I said.  ``Good luck with the booby traps.''  I hung up.



Then I looked down at Lung.  I drew my knife.



``Why the knife?'' Bitch asked.  I think anyone else might have sounded concerned.  She just sounded curious.



``I'm ending this.''



I grabbed one of the larger spikes that framed Lung's face and heaved it to one side so his accordion-like neck was outstretched, face upturned.



No time to be delicate about it.  I had no idea how strong the toxins in Newter's blood were, or how fast Lung's biology would process it.



I jammed the knife into Lung's eye socket.  His head and consequently his eyes weren't as large as you'd think, in proportion to the rest of his frame, but the tissue around it was tough.  I had to leverage the knife back and forth before I was able to pry his eyeball out.  It was hot to the touch as I held it in the palm of my hand, no bigger than a ping-pong ball.



The second eye was faster, though no less messy.



When I was done, I stood, sheathed my knife and backed away from Lung's body. Shouldn't I feel worse about this?  Shouldn't I feel sick, or grossed out, or disturbed by the morality of it?  I didn't even feel cold, the way Grue had described.  It just felt like something I had to do.



I glanced at the two eyeballs clasped in my hand, then put them out of my mind.  I surveyed the room.  Priorities?



I asked Bitch first, ``The dogs are okay?''  If I placed them second to anyone else but her, or if I forgot to ask, I got the feeling Bitch would mind.



``They'll heal when they turn back to normal.''



``Sundancer?'' I asked.



Sundancer was lying on her side, one arm pressed against the shoulder Oni Lee had stabbed.  ``I'm\ldots okay.''



That was everyone I gave a damn about, leaving only Fenja, Menja and Kaiser.  I looked across the room and called out, ``Fenja?''



The giantess nodded.



``Get your sister to a hospital, or whichever doctor your guys use.  Get your boss taken care of.''



She stood without giving me a response.  Her sister had shrunk enough for her to cradle in her arms.  Kaiser, for his part, was slung over her shoulder, limp.



``Oh, Fenja?''



She paused.



``I'll leave it to you to make the call, but if you think Kaiser has a sense of honor, maybe point out it would be bad form to push the point on the dogfighting thing, after we dealt with Lung for him, saved his life.''



She nodded, then ducked through the opening in the wall.



I stepped toward Sundancer and offered a hand to help her up.  She flinched away.



Oh.  My hands were bloody.  I dropped the offered hand to my side.



``Let's go,'' I suggested.





