





``Brockton Bay 911, what is your emergency?''



``Multiple injured,'' I said, glancing at the nearest street sign, ``Warehouse at Whitemore and Sunset.  Send police and capes, too.  These guys are ABB members.''



There was the briefest of pauses, ``That's Whitemore and Sunset?''



``Whitemore and Sunset, yes.  Listen, the leader of the ABB, a parahuman by the name of Lung, is incapacitated at the scene, but that won't be entirely true for long.  He's drugged and blinded, but the drugs will be out of his system before too long.''



``You're a cape?'' she asked, ``Can I get your identification?''



``I repeat,'' I ignored her, ``He's drugged and blinded, but only the blindness will be a factor when the first responders arrive on the scene.  Warn them to be careful.  You can also tell them that a second parahuman calling himself Oni Lee was present but fled after being injured.  He may still be in the area.''



``I understand.  The Protectorate will be informed before they arrive on scene.  I've got ambulances, police and PRT teams on their way.  Can I \emph{please} get your identification?''



I hung up.



``I can't believe you carved out his eyes,'' Sundancer said.  We were walking briskly back to where we'd left Labyrinth.



``He'll heal,'' I pointed out, ``Eventually.''



``You blinded someone who was helpless to fight back.  That's kind of fucked up.''



I couldn't say much to that.  Fucked up or not, it had been necessary.  I couldn't have dealt with it if I'd known we left him there and he got back to business as usual by the end of the day.  I'd stopped him, best as I was able.



Okay, alright, I was willing to admit that maybe the means were a little suspect.  I'd fought alongside some fucked up people, I'd maimed him.  By letting Fenja, Menja and Kaiser go I'd sort of condoned what they'd done to Lung's men.  But in the end, it was what I'd wanted to do when I'd wanted to be a superhero.  I'd taken down a horrible person.



I just hoped the heroes could clean up the mess and get Lung behind bars for good this time.



``Hey Bitch,'' I said, ``Why'd you come back?''  I couldn't phrase it better without offending her, but I wanted to know was why she'd come back when she was supposed to be taking Newter and Coil's soldier to a doctor.



Bitch was sitting tall astride Brutus.  She seemed to get my meaning, ``The other soldier said he was a trained medic.  Told me he could handle it, so I came back to fight.''



``Ah,'' I said.  ``Got it.''



Bitch hadn't been lying, I saw, as we approached the rest of our group.  Newter was bandaged and awake, while the other soldier was lying down, unconscious.  Maybe drugged for the pain.



``You made it,'' Newter grinned.



``Barely,'' I admitted, ``You okay?''



``I'm tougher than I look,'' he responded, ``Benefit of my, um, unique biology.''



``Cool,'' I replied, feeling lame for not having a better reply, but I couldn't think of anything to say that wouldn't sound like it was trying too hard or, worse, sound sarcastic.



``This fella says you guys probably saved my life,'' Newter jerked a thumb toward the one of Coil's guys that was awake.



``Honest, I'm having a hard time believing you're up and talking right now,'' the medic replied.



``Anyways, thanks,'' Newter said, eyes moving from me to Sundancer to Bitch and back again.



``No problem,'' I answered him, feeling lame for not having a better or more suitable reply.  Embarrased, I looked for a reason to change the subject.  ``Look, we should get out of here in the next few minutes.  Capes, cops and ambulances are on their way to deal with the aftermath.''



``Alright,'' Newter said, ``But I have to ask\ldots a small army of roaches dropped those off?''



He was smiling as he pointed to a spot near where he was lying.  A stack of paper bags were organized in a pile.



``I forgot I did that,'' I admitted, ``It didn't feel right to leave the ABB's money behind if we wound up retreating, so I had my bugs haul it out of there.  Everyone might as well take a bag.''



``We can take it?'' Newter asked, ``You sure?''



I shrugged in response.  The money didn't matter much to me.  ``Consider it a bonus, a thanks for helping.  It's, um, not exactly divided to be fair, so no insult intended if any of them end up being a bag full of ones.''



``No complaints,'' Newter said.  He reached out with his tail and used it encircle and pick up a bag.  Coil's guy gave him a hand in standing up, and you could see him wince and huff out a breath at the effort.  He swayed a bit on his feet, then put a hand on Labyrinth's shoulder to steady himself.  Sundancer grabbed a bag, and Coil's medic/spotter grabbed two.



Labyrinth didn't reach for one, so I walked over, grabbed one, and held it out for her.  She didn't respond.



``I'll hold that for her,'' Newter offered.



``Is she okay?''



``She's\ldots pretty much normal.  For her, anyways.''



He claimed the bag, leaving three for Bitch and I, but nobody was complaining or pointing that out.



``You guys need a ride?'' I asked.



Newter shook his head, then pointed to a manhole cover a ways down the road, ``We'll head back to one of our hideouts through there.  Familiar territory for me.''



``Is that a good idea, with your injury?  I mean, stating the obvious, but it's gonna be pretty gross down there.''



He smiled, ``Can't get an infection.  My biology's toxic to the bacteria and parasites, I think.  Never been sick, that I can remember.''



Of course.  Now I felt dumb for making Sundancer use the alcohol to sterilize him, and for going the extra mile with the sanitary pads, to ensure what I was using was clean.



``And you guys?'' I asked Coil's guy, ``Ride?''



``We've got one, but thanks.''  The medic bent down, bound his buddy's wrists, and then pulled the loop of arms over his head, so he was effectively giving his buddy a piggyback.  He took another second to arrange his guns, then headed through the same alley that Kaiser, Fenja and Menja had gone through before the fight started.



Sundancer was going the opposite way, so she said a brief goodbye and left.  Newter and Labyrinth were walking in the same direction as Bitch and I, so we walked together.



Labyrinth walked like she was in a daze, with Newter leading her along by the hand like she was a child.  It was interesting, not just to see that kind of interaction between them, but noting that her gloves looked like cloth, and that he was probably risking drugging her\ldots unless she was immune.  A consequence of her ability?  He caught me looking, smiled and shrugged.



``Autistic?'' I guessed.



He shook his head, ``No, though we thought that, at first.  Seems she was a normal kid until her powers showed up.  Since then, she's been off in her own little world, more or less.  A little worse right now, I think, after seeing me hurt.''



``That happens?'' I asked, gesturing towards my head, unable to come up with an inoffensive and simple way of phrasing it.



He shrugged, ``Sometimes getting powers fucks up your body,'' he gestured to himself using his tail, which was still holding the paper bags, ``Sometimes it fucks up your head.  Bad luck, but you deal with the cards you're dealt.''



``Oh,'' I replied.  I wasn't sure how to respond.  A cold, quiet horror crept up on me.  \emph{My} powers had something to do with my brain.  I could remember how crazy I'd felt right after my powers showed up, that torrent of nightmare images, signals and details from my bugs.  I still had bad dreams about it.  How close had I come to being like that permanently?



He grinned, ``It's cool.  She's really fond of us, and we're attached to her, too.  She has her lucid moments, when she's let us know she's cool with the status quo.  Sure, she has bad days when she's dead to the world, but all of our powers have drawbacks, yeah?''



``Yeah,'' I echoed him, though I couldn't think of a drawback to my power that even came close.



``I think we're okay where we're at.  Eh, L?  You've been happy since we got you out of that place?''



Labyrinth kind of stirred from her daze and looked at him.



``Yeah,'' Newter grinned, '' You can tell because the stuff she does with her power is prettier, these days.''  He gestured at the manhole cover, ``This is where we part ways.''



Labyrinth glanced down where he was pointing.  A moment later, a tracery of silvery lines spiderwebbed out around the manhole cover, extending and forking like veins.  As the lines met and sectioned off parts of the road, those bits of road lifted and flipped over, revealing a white marble texture on their undersides.  When sufficiently surrounded by the expanse of cracked white marble, the manhole flipped over, revealing a silvery underside, and then popped open on an unseen hinge.  A spiral stairway of more marble or ivory led down into the depths.  The white walls had a faint glow to them.



``Pretty cool, huh?'' Newter replied.  When he stepped down onto the stair, it was solid under his foot. He held up the paper bags as he said, ``Thanks guys.''



``Sure thing,'' I replied.  ``Later.''



The manhole shut behind them, and almost immediately, the white around the manhole began to fade.



I looked up at Bitch where she sat on one-eyed Brutus.  Angelica and a still-dusty Judas stood just behind her.  She offered me a hand up onto Brutus' back.



There were a lot of drawbacks to having a mask or helmet that didn't cover my entire head.  If I'd sat myself down and put in the extra hours to finish my mask and expand the armored sections, maybe I wouldn't have gotten that concussion that was proving to be such a pain in my ass.



The upside, though, was that it felt \emph{awesome} to have the wind blowing in my hair as we rode down the empty streets.  The perfect wind-down from that crazy adrenaline rush that had come with going up against Oni Lee and Lung within minutes of each other.  I closed my eyes and let the tension flow out of me.



We rode like that for a few minutes.  Bitch took turns and moved sorta aimlessly as she headed East, towards the water and the beaches.  Maybe she was taking evasive action in case we were being followed, maybe she just wanted to ride.  I didn't really care.



I was a little disoriented when we finally stopped.  Brutus padded through sand as he stepped down onto the beach.  Bitch hopped down, and I followed her cue.



It was still early afternoon, so the beach was deserted, and it wasn't the sort of beach that saw much tourist use anyways.  A concrete wall separated the beach from the roadside above us, and a yawning hole with the rusty remains of what had once been a grate marked the exit of the various storm drains beneath the Docks.  Trash, rotted leaves and one or two needles had filtered down to the sand below the drain.



``Go home,'' Bitch ordered the dogs.  One by one, they filed into the drain.  I guessed they would let the transformation subside before they returned to the loft on their own.



Then Bitch pulled off her mask.  She gave me a derisive look.



``What?''



``You gonna change?  Can't walk back like that.''



``I don't have a change of clothes with me.  Or stashed anywhere.''



``Well.  That's fucking stupid,'' she answered me.



``I wasn't thinking ahead when I decided to go.  Sue me,'' I challenged her.



``What're you wearing under that?''



``Tank top and stretch shorts.''



She looked around.  ``It's not that cold.''



I sighed and unstrapped my armor enough to unzip my costume at the back.  I pulled it off – far easier than putting it on – and bundled it up so all the identifiable parts of the mask and armor were hidden by fabric.  The sand was damp and clammy under my bare feet.



When Bitch reached for my face, I startled.  She put one hand on the side of my face, and for just a fraction of a second, I thought something incredibly awkward was about to happen.



Then she wrenched my head to enough of a tilt that it was almost horizontal.



``You look like someone tried to hang you.''



``What?'' I asked.



She touched the side of my neck, but it wasn't possible to see that part of myself without a mirror.  I did realize what she was talking about, after a moment's thought.  I pulled up the side of my tank top, and sure enough, there was a red-black bruise at my stomach and waist.  Hiking up my top a bit more, I found another at my ribs.  I knew there would be another up near my armpit, and one encircling my neck.



I had a giant fucking handprint on my body, courtesy of Lung.



I let out a long groan, touching my neck where I felt tender.  ``No way I can hide this from my dad.''



My good mood was dashed to the winds as we started trudging back to the Loft.  It was made all the more unpleasant because I was underdressed and barefoot, and the ground was cold under my feet.



I shivered and hugged my arms to my body as best as I could while still keeping my costume bundled up and the paper bags of money in hand.



Something warm settled over my shoulders.  I looked at Bitch as she finished draping her jacket over me.  As she drew back, her eyebrows furrowed, glaring at me, I wrangled the bags and my bundle of costume so I could get my arms through the sleeves and do up the buttons.  It was a canvas down jacket with a fur-ruff collar, but it was the wrong size for me and it was heavy.  The pockets, I found, as I tried to jam my hands in there, were filled with stuff.  A mess of plastic bags, chocolate bars, protein bars, a juice box, pellets that ground together – what I guessed were dog treats or dog food.  Not exactly cape supplies.  All in all, it was almost uncomfortable.



But it was warm.



``Thank you,'' I told her, floored by the gesture.



``You needed something to cover your neck,'' she looked bothered, ``People would stare.''



``Doesn't matter.  Thank you.''  I offered a smile.



``You already said that,'' she switched from looking bothered to looking angry, ``It's mine, I can take it back.''



``Of course,'' I said.  Then to be safe, I offered, ``Do you want to?''



She didn't reply, leaving me absolutely baffled.  Why was it that when I thanked someone like my dad for giving me a gift, it felt like it sounded sarcastic or lame no matter how I tried to say it, but the one damn time I was ninety-five percent sure I sounded as sincere as I felt, it was with Bitch, and she didn't buy it?



Worried anything I could say would rub her the wrong way, I defaulted to silence, as I found myself doing more and more often with her.  It wasn't a short trip, and my feet still felt the heat leeching out of them as I took each step on the pavement, but the core of my body was warm, and that was enough to keep me going.  Like that, we made our way back to the loft.



She unlocked the door and let us in.  I shouted up for Brian and Lisa, but no voices greeted me in return.  The others weren't back yet, which made sense, since Grue would have to pick up Tattletale and Regent before they got back, and it hadn't sounded like Tattletale's team was close to wrapping things up when I'd called.  Bitch led the way up to the Loft, and the second I was up there, I took off the jacket and wordlessly handed it to her.  She was still glaring at me.



What could I do, what could I say?  It seemed like everything I did pissed her off, sent the wrong signal.



I returned to my room in the Loft and dug through the shopping bags I still had in there, finding a loose pair of jeans and a long sleeved shirt to pull over my top.  No clean socks, sadly, but there were some covers laid out on the bed.  I grabbed some and dragged them behind me to the living room, where Bitch was watching TV.  She gave me the evil eye, but didn't complain, as I got myself bundled up in the covers on the other couch.



She had the remote, and I was willing to let her have it.  She channel surfed relentlessly, settling on an action movie for five minutes, then started surfing again when the ads started, and didn't go back to it.



It wasn't too interesting to watch, but I didn't mind.  I lay back, thinking back to the events of the day, the conversations, the tidbits of info.



I almost dozed off, when my lazy train of thought stumbled onto something that I was afraid I'd forget if I let myself go the rest of the way to sleep.  I forced myself to open my eyes and sat up a bit.



``Bitch?'' I risked drawing her attention, hoping she'd calmed down a bit.  She looked at me.



``Um.  When we were talking, a little bit ago, I thanked you.  Did that sound sarcastic to you, or what?''



``You're getting on my case again?''



``No,'' I raised my hands to stop her, ``Not what I was trying to do.  I'm just wondering.''



``Keep your wondering to yourself,'' she snapped.  When she turned her attention back to the TV, her channel surfing was cranked up a notch.



``I'll pay you to answer me,'' I tried.



She looked at me.



``That money we grabbed.  You can keep all of it.''



Her eyes narrowed, ``We're supposed to split our take five ways.''



``We earned that, right?  The both of us?  I won't tell the others if you don't. And I'm saying you can have it all.  Not sure how much it is, but it'd be yours.''



``Is this a trick?''



``No trick.  Just answer my question.  You can even tell me to get lost after, I'll go to my room and grab a nap or something.''



She leaned back, and put the hand with the remote in her lap, glaring at me.  I took that for consent.



``So, what I was asking before, when I said thanks, did you think I was sarcastic, did you think I was genuine, what?''



``Dunno.''



``You mean you didn't know, or you can't remember, or-''



``I said dunno.''



``Fine,'' I sighed, ``Whatever.  Money's yours.''



``That easy?''



I shrugged.



``You said you'd get lost if I asked,'' she pointed out.



I nodded, gathered the covers and retreated to my room.



I didn't nap, though.  Instead, I stared up at the iron girders that framed the ceiling, deep in thought, thinking about the conversation with Newter about Labyrinth.



I was still sorting through my thoughts when the rest of the gang returned.



I ventured out of the room, still bundled in a blanket, to greet them.  Brian gave me a winning smile as he pulled off his helmet, and I got some attention for having the most noteworthy injury of the afternoon.



As Alec, Brian and Bitch started talking about their individual adventures, Lisa pulled me aside.  We wound up walking to the kitchen.  Lisa put a kettle on as she asked me, ``You okay?''



``Not really hurt, ugly as this looks, and I think I'm feeling better about the school thing.''



``But you're distracted by something.''



``I was talking to Newter.  You know Labyrinth's kind of out of it, because of her power, right?''



``You want to know if there's anything wrong with you, that you don't know about?''



``No,'' I shook my head, ``Wait, is there?''



``Nah.  So what's up?''



``Bitch.''



``Ahhh.''



``I've been thinking, but I don't want to build up some theory in my head, make an assumption and embarrass myself.''



``Tell me what you're thinking, and I'll tell you if you're wrong.''



``She's really good at reading body language, right?  She could read Brian even when he was blurred by his darkness with a mask on.  It's, what, some kind of minor power of hers?''



``Some of it's natural ability.  Some of it's, yeah, that her power adjusted how she thinks.  So she can communicate better with her dogs.''



``Right,'' I glanced down the hall to where the others were talking.  Or rather, where Brian and Alec were talking and Bitch was standing there.  ``That's the thing.  What I'm thinking is\ldots maybe when her power gave her the ability to understand dogs, it overwrote something else?  Fucked up her ability to deal with people?''



Lisa turned and got some mugs out of the cupboard.  She gave me an apologetic half-smile. ``Yeah.  Something like that.''



``So, what, she can't read expressions, or tone?''



``All the cues we give to others as a part of regular conversation?  She doesn't get them, she probably couldn't learn them with a year of concerted effort.  It's not just that she doesn't get it\ldots the most basic interactions are messed up by the canine psychology that's hardwired into her head.  You smile at her and ask her how she's doing, her first thought is that you're baring your teeth at her in anger, and she has to remind herself you aren't.  But even after that, she's probably wondering if you were being sarcastic, or condescending, or kind, or whatever.  She knows you aren't shouting at her from your tone of voice, but we don't always raise our voices when we're angry, you know?''



``Yeah.''



``And she falls back on the one thing she does get, canine behavior, because it does work on a level.  Bids for dominance, eye contact, pack heirarchies and establishing territory, all adjusted and adapted to her human life.''



``So she's not really a sociopath.''



``No, not so much.''



``Why didn't you say anything?''  I realized belatedly, that I sounded accusatory.  Maybe I was right to.



``Because she'd leave if she heard about it, and for reasons \emph{I} don't know, the boss wants her to stick with us.  She's spent her whole life accepting the fact that she had a shitty childhood, and it made her into a screwed up person.  Her dogs are the only thing that's normal and right for her.  If she found out that the reason she's so messed up is \emph{the very same thing} that makes her so close to her dogs?''



She let the thought hang.



``Got it,'' I replied.



``So not another word of this, please, unless it's absolutely necessary and you're absolutely, one-hundred percent positive she's not going to overhear.''



``Do the others know?''



``I don't think it would change much, and I don't trust those two to keep a secret.  Brian is\ldots I don't want to say too honest.  But he's transparent, and Bitch can read him.  Alec would forget and let it slip as part of a joke.  He doesn't get the gravity of stuff, sometimes.''



``Okay.''



She poured a cup and stirred it, then handed me a mug of Ovaltine.  She got the other mugs arranged on a tray, and carried it through to the living room.  I stayed where I was, to think.



I was reminded of a non-fiction book I'd read where a kid got halfway through high school before his teachers realized he was illiterate.  He did it by being the class clown, by acting out.  Was Bitch the same?  The violence and hostility could be a cover to distract from her own inability to interact, at least partially.  I guessed a fair bit of it was genuine, though.  She \emph{had} had a crappy childhood, she \emph{had} lived on the streets and had fought tooth and nail to get by and avoid arrest.



But at the end of the day?  As awkward as I felt in day to day interactions?  She was a hundred times worse off.





