





``This what you wanted?'' the teenager with scruff on his chin and his hood up handed over the paper bag.



Broad hands with ruined, rotten brown fingernails pawed through the contents, ``It is.  Here.''  The voice was slightly accented, the words and sounds very careful, as though he were not comfortable with English.



The young man reached out and his eyes widened as a fold of bills was pressed into his hands.



``This is\ldots more than I thought it would be.''



``Are you complaining?''



The young man shook his head.



Gregor the Snail put his hands in his pockets, as if to hide the fingernails and the growths that scabbed the backs of his hands.  Each of the hard growths, which might have been shell or scale, none any larger than a silver dollar, had a prominent spiral shape to it.  As much as he could tuck his hands into his pockets, he was unable to hide his face.  He had no hair on his head, not even eyebrows or eyelashes, and the hard growths crusted his face like a terminal case of acne.  Most strange and disconcerting of all was the fact that his pale skin was translucent enough that one could see shadows of his skeleton, his teeth and the tongue in his mouth.



``As you can see,'' Gregor said, without any affectation, ``It would be hard for me to walk into a store and make simple purchases.  I do not like to rely on my friends for this.  Makes me feel indebted to them, and this is not good for friendships.  If you are interested in repeating this sort of transaction, being on call to run errands for me for a time, it could be arranged.''



``Really?'' the guy rubbed his chin, ``For how long?''



``Until I called and you were unable or unwilling to run my errand.  If this happened more than once, or if the reason was not good, I would find someone else, as I did with the last individual.''



``You didn't hurt him or anything?''



``No.  I did not.  He decided he would rather spend the evening with his girlfriend.  I have not called him again.''



``This won't be anything illegal?''



``No.  No drugs, no prostitutes, no weapons.''



``So you call me, I run out and grab you groceries, or clothes, or take-out, or shampoo, or whatever, and you pay me three--''



``That is four.  And I do not have hair, so you would not need to concern yourself with shampoo.''



``Right.  Sorry.  So, four hundred dollars each time?  What's the catch?''



``No catch.  I have money, I like things to be convenient.  Only one small chance of trouble.  My first assistant, she quit because she was concerned that my enemies would use her to get to me.  I will not deny this is possible.''



``You have enemies?''



``Yes.  But there has not been a case yet where any of my assistants ran into trouble with them.''



``Have any of them run into trouble at all?''



``The last assistant, the boy with the girlfriend.  He thought he could get more money, because he could go to the police and tell them what he knew about me.  He was lucky to try this when I was in a generous mood.  I dissuaded him.  He worked for me for two months after that with no complaint.  We were not friendly, it was pure business.  I would recommend, gently, that you not try the same thing.''



``Hey.  Live and let live, right?''



``That is a good saying.''



``Okay.  I'm wanting to go to college this fall, and this is sounding a hell of a lot better than working minimum wage for fifty hours a week.  Here, my cell phone number,'' he handed over his phone.



Gregor the Snail took a second to put the number in his own phone.  ``I have it.  I will call.''



They parted ways.



Gregor walked down the side streets of downtown Brockton Bay with the hood of his sweatshirt casting his face in shadow.  Anyone who happened to cross his path and look beneath his hood were quick to glance away.  Embarrassed, spooked.  Those that saw him from a distance knew him as monstrous as well, but in a different way.  To them, he was simply one of the morbidly obese.  A man in his late twenties or early thirties, nearly three times the weight he should be for his five feet and ten inches of height.  His weight, he knew, was one of the rare things in this modern world that someone could use to mock him openly.



It had taken him years to come to peace with this.  With being one of the monsters.



As he came to his destination, the throbbing pulse of music reached his ears.  The club sat two blocks away from Lord Street, and there was a line extending around the side of the building.  Glowing yellow letters in an almost intentionally plain script spelled out `Palanquin'.



He skipped the line and headed straight for the front door.  A burly Hispanic doorman with a beard tracing the edges of his jaw undid the chain fence to let him through.



``What the hell?'' one of the girls near the front of the line complained, ``We've been waiting for forty five minutes and you let that fat fuck through like that?''



``Out of the line,'' the doorman said, his voice bored.



``The hell?  Why?''



``You just dissed the owner's brother, fuckwit,'' the doorman told her, ``Out of the line.  You and your friends are banned.''



Gregor smiled and shook his head.  The line the doorman had pulled was bullshit, of course, he wasn't the owner's brother.  But it was nice to see one of the assholes getting what was coming to them.



He had worked as a bouncer for clubs that wanted someone more exotic and attention-getting, way back when he was first getting on his feet, so he knew that the line you saw out the door was rarely an indication of how many people were inside.  An empty club could have a line of people waiting to get in, to give the right image.  Even though it was a Tuesday night, Palanquin had no such need for such deceptions.  It bustled with people.  Gregor carefully navigated the crowd of dancers and people holding drinks, until he reached a stairwell guarded by a bouncer.  As with the front door, his admittance to the stairs was automatic, unquestioned.



The upstairs balcony wasn't filled with people, and those that were present, a dozen or so, were almost boneless in their lethargy.  Mostly girls, they lay prone on couches and in booths throughout the balcony that overlooked the dance floor.  Only three people were more or less alert as Gregor approached.



``Gregor, my boy!'' Newter grinned from ear to ear.  Gregor caught the briefest flash of disgust on the face of one of the girls sitting with Newter, as she looked at him.  She was a blonde with blue lipstick and pink highlights in her hair.  Had Gregor been working as the doorman, he would have checked her ID, double checked it, then even if it did look real, he would have kicked her out anyways for being too young.  She couldn't have been older than sixteen.



Still, that was roughly how old Newter was, and he could hardly fault the boy for being interested in someone his own age.



The other girl, dark haired, had a European cast to her features.  She showed no such distaste.  When she smiled up at him, there was no sign the expression was forced.  That was both rare and interesting.



``I brought your dinner,'' Gregor said.



``Good man!  Pull up a chair!''



``The others will want their food as well.''



``Pull up a chair, come on.  I've got two stunning girls here, and they're not believing me when I'm telling them about some of the cooler jobs we've pulled.  I need backup here, bro.''



``I do not think it is a good idea to be talking about these things,'' Gregor said.  He stayed standing.



Newter reached for the bag and grabbed a sandwich from inside.  ``It's cool.  Faultline joined the conversation a while ago, so she's obviously okay with it.  You aren't going to tell, right, Laura?  Mary?''



Each girl shook her head as Newter asked them by name.  That let Gregor label the dark haired girl as Laura and the girl with the blue lipstick as Mary.



``If Faultline said it was fine.'' Gregor said.  He took the bag back from Newter and found his own sandwich.  ``Laura and Mary, I am sorry, the other sandwiches I have here are spoken for.  I could offer you some of my own, if you would like.''



``That's okay, I'm not hungry,'' Laura replied, ``I like your accent.  Is it Norwegian?''



Gregor finished his first bite, swallowed, and shook his head, ``I am not sure.   But I have spoken to an expert and he says the other language I speak is Icelandic.''



``You don't know?''



``No,'' Gregor replied.



His brusque answer only stalled the conversation for a moment before Newter got it going again, ``Okay, bro, tell these girls who we went up against last month.''



``The toybox job?'' Gregor asked, ``With the Tinker black market?  There was nobody--''



``The other one.  The job in Philadelphia.''



``Ah.  Chevalier and Myrddin.''



Newter clapped his hands together, rocking back in his seat, ``Told you!''



``And you beat them,'' the dark haired girl said, disbelieving.



``We didn't lose!'' Newter crowed.



``It was a close call,'' Gregor added his own two cents.  ``Chevalier is leader of Protectorate in Philadelphia.  Myrddin leads Protectorate of Chicago.  These are people whole world recognizes.  They got positions protecting big cities in America because they are strong, because they are smart and talented.  We got the job done, as we always do, and we walked away.''



Newter laughed, ``Pay up.''



Neither Laura nor Mary looked bothered as they reached into their pocket and purse, respectively, and fished out some bills.



``What was the bet?''  Gregor asked.



``I told them they didn't have to pay if I was lying.''



``And if you \emph{weren't} lying?  They pay more?''



``No penalty.  I got company and conversation for a while,'' Newter smiled.  He reached up to the back of the booth, grabbed a bag that sat there, and fished out a pair of plastic spoons and a bottle of water.  With a water dropper he retrieved from his pocket, he siphoned water from the bottle and placed a few drops in each spoon.  The final step was dipping the tip of his tongue in each drop of water.



``Lick it up,'' he told the girls.



``That's all?''  Laura asked him.



``It's enough.  Any more and you might be out for an inconveniently long time.  That right there,'' Newter pointed to the spoon with the tip of his tail, ``Is a little less than an hour of psychadelic tripping.  No hangover, no side effects, it's not addictive, and you can't overdose on it.  Trust me, I've tried to make someone overdose before, combat situation, and I couldn't make it happen.''



Mary was the first to take the spoon and pop it into her mouth.  Moments later, her eyes went wide, and she fell limp against the back of the booth.



``Hey,'' Laura said, turning to Gregor.  She reached into her pocket, found a receipt and a pen, and scribbled on the blank backside of the paper.  She handed it to him.  ``My number.  If you want to talk, or, you know, something else.''



She winked at him, then popped the spoon into her mouth.



Gregor blinked in a mild confusion as her head lolled back.



``Looks like you made a good impression, Gregster,'' Newter chuckled.



``Maybe,'' Gregor said.  He put the half of his sandwich that remained back in the paper bag, then balled up the wrapper.  After a moment's hesitation, he crumpled the receipt with Laura's number into the ball.  He pitched it to a trash can halfway across the room.



``Hey!  What gives?''



``I do not think she liked me because I am me,'' Gregor said, ``I think she liked me because I am a monster.''



``I think you're sabotaging yourself, man.  She's hot.  Look at her.''



Gregor did.  She \emph{was} attractive.  He sighed.



``Newter, do you know what a devotee is?''



Newter shook his head.



``It is a slang term for someone who is attracted to people with disabilities, \emph{because of the disability}.  I think it is about power, attraction to someone because they are weak somehow.  I think it likely that this Laura sees me as weak because of the way I look, the way I may have trouble day to day, and this is compelling to her in a similar way to how a cripple or a blind man might be to a devotee.  This does not appeal to me.''



``No way.  Maybe she likes you because of the person underneath.''



``She did not see enough of me to know who that person might be,'' Gregor replied.



``I think you're doing yourself a disservice.  I'd jump on that opportunity.''



``You are a stronger person than I in many ways, Newter.  I should bring the others their dinner,'' Gregor turned to leave.



``Hey, signal Pierce downstairs to send another girl or two up, will ya?''



Gregor did as he was asked, getting the attention of the bouncer at the foot of the stairs.  The bouncer, in turn, got the attention of a set of girls on the dance floor.



While the girls made their way up, Gregor turned to Newter, ``Are you happy?''



``Oh man.  You're not going into a philosophical phase again, are you?''



``I will spare you that.  Are you?''



``Dude.  Look at me.  I have money to burn, I've got the hottest girls in the city begging to get a taste of me.  Literally wanting to taste me!  What do you think?''



``You are happy, then?''



``Time of my life, bro.''  Newter opened his arms wide to greet a trio of girls as they reached the top of the stairs.



``I am glad.''  Gregor turned and entered the hallway at the back of the balcony.  As the door sealed shut behind him, the pounding of the music behind him dimmed.



His next stop was the first door on his left.  He knocked.



``Come in.''



The bedroom had a bed on each side, in opposite corners.  One side of the room was cluttered with posters, pictures, a bookshelf overflowing with books, an Apple computer with two CD racks towering above it, and two speaker systems.  The music from the computer speakers only barely managed to drown out the music from the club downstairs.  The girl who was lying back on the bed had a dense covering of freckles on her face and hands, and curly brown hair.  Magazines were piled in stacks around her on the bed, threatening to topple over at the slightest movement.



The other side of the room was spartan.  Nothing adorned the walls, there were no books, no computer or computer paraphernalia.  There was a bed, a bedside table and a dresser.  The only character whatsoever was a colorful bedspread and pillowcase.  Gregor knew it had been a gift from Faultline.  The owner wouldn't have gone out to get it herself.  The resident of that side of the room was seated in the corner, staring into the wall.  She was blonde, the sort of platinum white-blond hair that rarely lasted through puberty.  Her royal purple sweater was slightly too large for her, drooping over her hands, and her pale jeans were clearly intended to be more comfortable than fashionable.



``I brought your dinner, Emily.''



``Thanks,'' the freckled girl answered him.  She caught the sandwich he threw to her and began to peel open the package.



``Is she okay?'' he asked, gesturing to the girl in the corner.



``Not one of her better days.''



He nodded.



``Elle,'' he spoke, gently, ``May I come closer?''



They had learned the hard way, that the more distant the girl was, the stronger her power.  This made her particularly dangerous when she was so lost that she might not recognize him.  Cruel irony, Gregor observed, that she had virtually no power at all when she was most herself.  It was a problem they hoped to find an answer to, someday.



The girl in the corner turned to meet his eyes.  He took that for consent, approached her, and pressed a sandwich into her hands.



``Eat,'' he instructed her.



She did, almost mechanical in her movements.



After Faultline had enlisted him and Newter, a job had taken them into a high security asylum.  They had been there to question someone about the Dragonslayers, a villain group that used tinker technology stolen from the most powerful and highest profile tinker in the world for petty theft and mercenary work.  Their invasion of the asylum had not gone as well as it might have, and had led to a high-tech lockdown of the facility.  Not only did it extend their mission by several hours, but it had led to issues with one of the residents, a parahuman that apparently had to be moved regularly, lest her influence over her surroundings spread beyond the confines of her cell, making her a serious problem for the staff, other residents and unwitting bystanders.



In the end, after dealing with the dispatched squad from the Boston Protectorate and getting the information they needed about the Dragonslayers, they had recruited the girl.



He watched and waited long enough to ensure she was on her way to finishing her sandwich, then turned to leave.  Emily gave him a small wave of the hand in goodbye, and he nodded once in acknowledgment.



His final stop was the office at the end of the second floor hallway.  He peered in the window, then let himself in as quietly as he could.



Faultline, owner of Palanquin and several other cover businesses across Brockton Bay, was seated at a large oak desk.  In front of her, in the midst of ledgers, notebooks and university textbooks, was something that looked similar to a xylophone, a series of rods lined up next to one another, strapped tight to a board.



Faultline was in her professional clothes; a white dress shirt with the sleeves rolled up and black slacks tucked into shiny black riding boots with steel toes.  Her wavy black hair was tied back in a ponytail.  She wore no mask – those employees of Palanquin who ventured as far as this office were too well paid to turn on her.  Her features were perhaps too sharp to be called conventionally attractive, but Gregor knew she was certainly more attractive than Newter or himself.



As Gregor watched, she closed her eyes, then swiped her hand across the top ends of the rods.  Red and blue energy crackled, and coin-shaped pieces of wood, metal, stone and plastic fell to the desktop.  Other rods, several of which were green wood, were untouched.



``Fuck,'' she muttered.  She swept the coin shaped bits of various materials into a trash can that sat beside her desk.  Glancing up at where Gregor stood just inside the doorway, she raised one eyebrow.



``I did not wish to interrupt you.''



``Don't worry about it.  Maybe distracting me will help.''



``If you are sure.''  He approached the desk, setting the paper bag down on it, ``It was seven o'clock, nobody had eaten yet.  I got us some sandwiches.''



``Thank you.  How's Elle?''



``Spitfire said she was having a bad day, but she has eaten now.  Perhaps tomorrow will be better.''



Faultline sighed, ``Let's hope.  It's very easy to let yourself grow attached to that girl, know what I mean?''



``Yes.''



``Fuck!'' she swore, as she swiped her hand over the rods and, again, the green wood refused to be cut.



``What are you doing?''



``We've talked about the Manton effect.''



``The rule that prevents some powers from affecting living things.  You have been trying to remove such restrictions from yourself.''



``Without luck.  It's a matter of time before we're on a job, things come down to the wire, and I'm too weak, because of this arbitrary limitation.''



``I find it hard to believe that anyone who has toppled a building on someone could call themselves weak.''



``That was luck more than anything else,'' she sighed, as she adjusted the positions of the rods.



``If you say so.''



``It's not like there isn't precedent for this.  We know for a fact that some capes who were once held back by the Manton effect have figured out a way around it, or past it.  Narwhal being the most obvious case.''



``Yes.''



``There's a school of theory that says that the Manton effect is a psychological block.  That, because of our empathy for living things, we hold back our powers on an instinctual level.  Or, maybe, we hold back against other living things because there is a subconsciously imposed limitation that prevents us from hurting ourselves with our own powers, and it's too general, encompassing other living things instead of only ourselves.''



``I see.''



``So I'm trying to trick my brain.  With this setup, I move from inorganic material to dead organic material to living tissues.  Green wood, in this case.  Or I mix it up so it goes from one to the other without any pattern.  If I can trick my brain into slipping up, anticipating the wrong material, maybe I can push through that mental block.  Do that once, and it'd be easier for future tries.  That's the theory, anyways.''



She tried again.  ``Fuck!''



``It does not seem to be working.''



``No kidding.  Do me a favor.  Rearrange these.  Don't let me see them.''



He approached the desk, unstrapped the rods, shuffled them, and then strapped them in place while she sat there with her eyes closed.



``Go,'' he told her.



She tried again, eyes still closed.  When she opened them, she cussed a few times in a row.



Gregor stepped around the desk, grabbed her by the throat with his left hand, and pulled her out of the chair.  He shoved her to the ground and climbed atop of her so he was straddling her, his knees pressing her arms down.  His grip tightened incrementally.



Faultline's eyes widened and her face began to turn colors as she struggled.  She brought her knees up into his back, but one might have had more success hitting a waterbed.  The effect was the same.  Beneath his skin, which was tougher than one might guess, his skeleton, muscles and organs all sat in a sea of viscous fluids.  His skeleton, he'd learned, was more like a shark's than a human's.  It was a flexible cartilage that bent where bone would break, and healed faster than bone.  He'd been hit by a car and climbed to his feet shortly after.  Her kicks would not have much effect.



``I am sorry,'' he told her.



Her struggles gradually became weaker.  It took some time before she started to go limp.



He waited a second longer, then released her.  She sputtered into a cough as she heaved air into her lungs.



He waited patiently for her to recover.  When she looked more or less in control of her own breathing, he spoke, ``Months ago, we were talking about this subject, the Manton effect.  You mentioned how it might be possible for someone like us to have a second trigger event.  A radical change or improvement in their powers as a result of a life or death moment.  Such might explain how one broke the Manton rule.''



She nodded, coughing again.



``It would not have worked if I had warned you in advance.  I am sorry.''



She shook her head, coughed once, then answered him, her voice hoarse, ``It didn't work anyways.''



``I'm sorry.''



``What if it had worked, you big lunatic?  What did you expect me to do to you?  Cut off your hand?  Kill you?''



``I thought perhaps my hand or my arm, at worst.  I do not think you would kill me, even in a moment such as that.  You have done much for me.  Even if it proved impossible to reattach, I would not say it is a very attractive hand,'' he examined the hand he'd just used to strangle Faultline, ``To lose it, for something you have been working on for a long time is not a regrettable thing.''



``Idiot,'' she pulled herself to her feet, coughing again, ``How the hell am I supposed to get pissed at you when you say something like that?''



He stayed silent.



``Well, either that's not going to work, or I need something that gets me even closer to death\ldots in which case I'm scratching it off the list anyways.'' She moved her chair and sat down at her desk, shoving the apparatus with the rods into the trash.  ``I like being alive too much to dance on that razor's edge.''



``Yes,'' his voice was quiet.



``Thank you, by the way, for trying that'' she told him, as she emptied the bag of one and a half sandwiches.  She returned Gregor's half-sandwich to the bag and put hers aside, unopened.  ``I don't expect it was easy.''



He shook his head.



``So, returning a favor, then.  Sit down.''



He pulled a chair over and sat on the other side of the desk.



``A year ago, you agreed to give me a share of your earnings in our little group, if I put them towards answering some questions we had.''



``I remember.''



``I'll talk to the others about this, soon, but since you were the one that paid the most, I thought it only right that I share with you first.''  She opened a drawer and retrieved a file.  She pushed it across the desk.  ``This is what I've found, so far.''



He opened the file.  The first page was an image, high resolution, of a stylized `u', or a `c' turned ninety-degrees counter clockwise.  He touched his upper arm, where a tattoo identical to the image marked him.



``Whoever it is,'' Faultline explained, ``Whether it's one person or many, is very, very good at covering their tracks.''



He turned the pages.  The next set of pages were pictures, crime scene reports, official files and news articles about various parahumans, each set of pages relating to a specific one.  The first was a monster of a man with a beetle-like shell covering his body.  Gregor himself was the second.



``You and Newter, you already know, aren't alone.  On a steady basis, parahumans have been turning up across North America.  Retrograde amnesia, all marked by that same tattoo as you are on various parts of their body.  Each was dumped in an out of the way location in an urban area.  Alleys, ditches, rooftops, under bridges.''



``Yes.''  Gregor turned more pages.  Each set of pages had more individuals like him.



``Here's the thing, though.  At first, most were strange in appearance.  As many as four out of five monstrous parahumans, if you'll excuse the term, follow the pattern, and that number might increase if you got a chance to examine or get a decent interview with the others.  The tattoo, amnesia, their first memories are waking up somewhere in a strange city.''



``At first, you said?'' Gregor asked, ``This changed?''



``Turn to the red tab.''



He found the red tab that stuck out and turned to that page.  A high quality picture of an attractive redheaded girl.



``She showed up in Vegas.  The whole casino thing has bitten the dust, pretty much, since parahumans who could game the odds or cheat started showing up.  But there's underground games, still.  She participated in a few, and had a bounty on her head in a matter of days.  She's calling herself Shamrock, and I'd put good money on the fact that she's got powers that let her manipulate probabilities.''



``I see.  Why are we talking about her?''



``Next page.''



He turned the page.  ``Ah.''



It was a grainy surveillance camera image.  Shamrock was in the midst of changing clothes in what looked like an underground parking lot, and, though partially obscured by her bra strap, the tattoo was visible on her shoulderblade.  A stylized `u'.



``That's puzzle piece number one.  Given the dates, and you're free to look them over in your own time, going by the first sightings, the people that are showing up with these tattoos are getting less and less monstrous with each passing year.  Not always, but it's a trend.  Then, boom, we get Shamrock.  No strange features to speak of.''



He turned ahead a few pages.



``Puzzle piece number two.  I'm afraid it's one of those cases where things have been covered up too well for us to verify, but I'll tell you what I heard.  Tallahassee, Florida, just three months ago, a rumor circulated about someone calling themselves the Dealer.''



``What was he dealing?''



``Powers.''



``Powers,'' Gregor echoed her.



``Pay him an amount in the neighborhood of thirty five thousand dollars, the Dealer gives you something to drink, and you join the ranks of the heroes and villains in the cape community.  Powers in a bottle.''



``I see.  How does this relate?''



``Because one individual claiming to be a customer made a blog post about his transaction.  It's near the end of that file.  In his post, he described the Dealer as having a metal suitcase filled with vials. Engraved on the inside of the lid\ldots''



``The same symbol as the tattoo,'' Gregor guessed.



Faultline nodded, ``And that's where we stand.''



``I see.  Can we track down this individual with the blog?''



``He's dead.  Murdered by two unnamed capes less than a day after he made the post.''



``Ah.''



``What I think is that someone out there has figured out how people get powers, and they've made a business out of it.  But the first attempts didn't go so well.  It could be that, if the chemistry is bad, the people who drink the stuff become like you, like Newter, like Sybill and Scarab.''



``So this person, or people.  You think they are experimenting.  They have been refining their work, and the physical changes have become smaller.''



``And this Dealer was either their salesman, or more likely, someone who stole some of their work and tried to profit from it.  The people he dealt to didn't get the tattoos.''



Gregor's chair groaned painfully as he leaned back.



``What is next?''



``No one's seen or heard of this Dealer since the blog poster was murdered.  The Dealer's either dead or gone to ground.  So we follow our other lead.  I've got private investigators looking for Shamrock.  I'm thinking we wrap up our contract with Coil, here, then, if we're lucky enough that our PIs find her before the bounty hunters do, we pay her a visit. Either she can tell us something, or we can offer her a position on the team.''



``Or both,'' he said.



``In an ideal world,'' Faultline smiled.





