





Tattletale stirred.  I could see the usual confusion that went with waking up in unfamiliar surroundings.  She adjusted faster than most.  There was no flailing about for a point of reference so everything could start to make sense again.  Her power supplied it.



``Hey,'' she said.



``Hey,'' I replied.



``Think the world's going to end today?''  she asked, as she stretched, still lying down.



``World already ended, if we're talking about \emph{our} world.  Too much damage done.''



``Maybe,'' she said.  ``Humans are resourceful.  Resourceful and stubborn.  But you kind of live that, don't you?''



I nodded.  ``Guess so.''



Tattletale picked a bit of grit out of the corner of her eye with a fingernail.  ``You didn't sleep.''



``Not so much.''



``Idiot.''



``I've learned to deal.  Pulled enough stakeouts to adapt.''



``Idiot,'' Tattletale said again.  She raised herself to a sitting position.  ``You need to be in top fighting shape.''



``I slept for three days after getting cut in half,'' I protested.



``Only shows how much you needed the sleep,'' she said.



``The Simurgh was being eerie, singing you a lullaby.  You really expect me to sleep after that?''



``The lullaby wasn't for me,'' Tattletale said.  ``And I didn't sense any hostile intent.''



I turned my head.  My expression was hidden, but she read my confusion anyways.



``I mean, I think \emph{some }of it was for my benefit, but it didn't fit like that was the be-all and end-all of the singing.  She was doing something else.''



``I don't get it.''



``Neither do I.  But she's not exactly an easy one to get.  Who knows what she sees?  Maybe she's singing for a reason that isn't apparent yet?''



\emph{That} was unsettling.  I thought of what the Simurgh had said.



It didn't serve to keep secrets right now.  It'd be disastrous in the worst case scenario, and Tattletale was the best person to go to when I needed answers.  ``She apologized.''



``The Simurgh?'' Tattletale asked.  She gave me a funny look.



``Believe it or not.  She said `I'm sorry'.''



``She doesn't talk,'' Tattletale said.



``I know.  But I heard it.''



``Anyways, she isn't sorry,'' Tattletale said.  ``I'd put money on it.  I've got a \emph{lot} of money to put on it, if anyone's willing to take the bet.  Couple million in liquid assets.''



I shook my head.  ``I won't take that bet.  Look, just keep it in mind.''



``Filed away,'' Tattletale promised.



``For now though, we should mobilize,'' I said, as if I could distract myself.  ``Get everyone on the same page, start putting heads and powers together.''



``Sounds like a plan,'' Tattletale responded.  She pulled off a glove, then reached into her belt to get a small tin from one pouch.  ``Two minutes to get myself presentable.  Could do with a shower, but I think people are a little past that right now.''



I nodded.  Most of the capes I'd seen were just a little rougher around the edges.  The shine gone from their costumes, a little dustier, their hair greasier, chins unshaven.  Psychologically, it was much the same.



This had hit all of us hard.  I liked to think I was rolling with it better than some, if only because I'd had two years to anticipate it.  Then again, I was good at self-delusion.



I thought about Clockblocker, his optimism.  When I'd been talking about expecting the worst, he'd argued for the opposite.  I didn't want to diminish what I felt about him being dead in the general sense by thinking about something so petty, but a part of me was disappointed I couldn't talk to him now, after the fact, and see how he was doing.  If he was coping better than I had.



It wasn't that I was coping, exactly.  I wasn't happy, confident or unafraid.  The only thing I could say was that I'd been able to brace myself.  I'd bought into Dinah's prophecy more than just about anyone else.  I'd braced myself and I'd nearly broken, regardless.  I could tell myself that the point where I'd been floating over the ocean by New Brockton Bay had only been a desire to get away, nothing darker, but I wasn't sure I was telling myself the truth.  I could think back to the point where I'd snapped after being cut in half by Scion and tell myself I was lucid, but I wasn't sure \emph{that} was true either.



Hard to say I'd held my own when I wasn't sure how much of it was \emph{me} and how much was the adrenaline at work.  Or other things.



\emph{Any opinion, passenger}?  I asked.  \emph{We're going up against your maker.  You going to hold back or are you going to go all-out?}



No response, of course.



Tattletale was smearing black greasepaint around her eyes.  She'd finished the hardest part, around the eyelashes, and spoke up as she filled the rest in,  ``You get in touch with everyone you wanted to talk to?''



``Almost everyone.''



``Ah.  I can guess who you didn't actively look for.  This denial worries me.''



I shrugged.



``No use dwelling on it.  Your decision in the end.  Let's move on to a happier topic.  You ever think we'd make it this far?''



``To the end of the world?''  \emph{That's a happier topic?}



``To the top of the heap.  As far up there as we could hope to be.''



``We're not big leaguers, Tattletale.  Not the most powerful capes out there.''



``But we're talked about around the world.  We're on speaking terms with some of the biggest and scariest motherfuckers out there.''  Tattletale gestured towards the window.  Towards the Simurgh.  ``We'd be front page news, if the news still existed.''



``I'm not sure being news would be a good thing,'' I said.  ``Which isn't to say word isn't getting around, you know.  \emph{Charlotte} knew.''



``Charlotte's connected to Sierra and the rest of our infrastructure in Gimel.  That doesn't really surprise me,'' Tattletale said.  She pulled her hair out of the loose ponytail she'd had it in, then combed her fingers through it to get it more or less straight.  It still had kinks and waves where it had been braided.  Something she would have fixed before going out in costume in more ordinary circumstances, for caution's sake.



``Mm,'' I acknowledged her.  Maybe I was tired.  My thoughts were wandering some.



``I tried to set things up so we'd have some way of maintaining communications and getting \emph{some} information in, getting information out.  Like, I told people about what you said about Scion hating duplication powers.  Anyways, only the very high tech and very low tech have really survived.  Satellites and hard copies.''  She lifted one of the files I'd stacked on the floor, as if to give evidence to the point. ``Reading up?''



I picked up a file as well, leafing through it.  ``I wasn't sleeping, so while you were out, I got in touch with Defiant and one of your minions, arranged for only the most essential status updates to come in on paper.  I figured I could update you after you got up.  The deliveries stopped a good bit ago, but one of the last status updates was about Dragon, so I guess she's handling her old duties while Defiant recuperates from the last few days.''



``Guess so,'' Tattletale said.  I turned my head to see what she was doing, but she was already crossing the room.



``Doormaker is napping as well, I guess,'' I said.  ``He just decided to leave one open, and he hasn't been responding.  I double checked the portal, making sure he wasn't trying to tip us off to anything important, but it opens to a pretty remote area of Earth Bet.''



Tattletale went still, ``Doormaker doesn't sleep.''



I raised my eyebrows, realized Tattletale couldn't see them, and cocked my head quizzically instead.



``There're lots of capes who don't sleep.  About a year ago, I started digging into the PRT files.  Hired the Red Hands to steal a more up to date set, even.  I was looking into clues for understanding this whole thing, y'know?  Best leads at the time were memories and dreams.  Clues popping up here and there, relating to people's dreams, or gaps in memories.  Dreaming differently, seeing things instead of dreaming, case fifty-threes suffering from their amnesia\ldots Well, there are a number of `Noctis' cases.  Named after a vigilante hero that was up at all hours.  The opposite of what I was looking for, but a good data point anyways: capes who don't dream because they don't \emph{sleep}.  PRT confirmed a few members of their own, Miss Militia included, as examples.  Others have only been marked down as guesses.  Doormaker and Contessa were among them, they said, going by the times the `bogeyman' was showing up.''



``So if he doesn't sleep, why leave a door open and ignore us?'' Tattletale asked.



I shook my head a little.



``Doorway,'' Tattletale tried.



There was no response.  No portal, no door.



``Door?  Portal?  Open sesame?''  I tried.



``That's worrisome,'' Tattletale said, keeping her voice low.  She clipped on her belt, tapping each of the pockets, as if to check the contents were still there.  She drew her gun and checked it for bullets.



``We should go,'' I said.



``We're \emph{definitely} going,'' Tattletale said, but she didn't budge as she double-checked her gun, pulling the slide back.  I resisted the urge to comment on just how useless a gun was, considering what we were up against; I could remember how she'd fared when the assassin targeted her, Accord and Chevalier.



There were other threats.



``Right,'' Tattletale said, finally finishing, grabbing her laptop and tucking it under one arm.



That was our \emph{go} signal.  We broke into stride.



We passed a soldier, and Tattletale signaled him, raising a finger.  He stopped and wheeled around, following.



``We're going,'' Tattletale said.  ``Ship up, move out.  If we come back and settle in here, then so be it, but let's not plan on it.''



``Yes ma'am.''



``Get someone to collect my things.  All the files, the computers, the food.  Everything.  Get it all to the far side of the little doorway\ldots''  Tattletale looked at me.  ``Where's the doorway?''



``A bit outside the front doors,'' I said.



``What she said,'' Tattletale told her mercenary.  ``If we're gone, just hold position.  If we're still gone after twenty four hours, assume we're dead.  Get my data and the backups of my notes to someone who matters, then consider the job done, collect your payment, go on your merry way.''



``I'll make sure everyone's informed.''



``Do,'' she said.  Then, as if to offset the curt command, she added, ``Thanks, Tug.''



He gave us a sloppy salute as he broke away, turning down a different corridor.



I had my phone out before I was outside.  My bugs let me navigate the stairs without taking my eyes from the screen, as I input commands.  It was cold out, almost cold enough it would impair my bugs, and a heavy fog hung in the open clearing.  The stout military building stood in an open, overgrown grassland, encircled by evergreen trees.



No reception.  Not a surprise, but inconvenient.  I watched as we got closer to the portal Doormaker had left open.



Tattletale, for her part, turned around, walking backwards as we reached the bottom of the steps.  With the phone still dark, I took a moment to look in the same direction.  I was treated to the intimidating image of the Simurgh passing over the building.  She moved as if she were as light as a feather, but I knew that wasn't true.  She was heavier than she looked, by a considerable margin.  Had she set her full weight on the roof, she would plunge through.



Like someone playing hopscotch on the moon, the Simurgh set one foot down on the roof, hopping forward, set another foot on the very edge and pushed herself off.  She floated down to the space beside the portal, then unfolded her wings, drawing the halo out to its full breadth.  The movements sent swirls of dust and fog rippling across the edges of the clearing, stopping only as they crashed into the line of trees.



``She changed the guns?'' I observed.



``She did,'' Tattletale observed, ``Cosmetic changes.''



Each of the Simurgh's guns had been streamlined, the outer casings, barrels and handles reworked into wings.  Three concentric circles of interconnected guns, all redesigned to appear like an extension of her own wings, behind her.



``Why cosmetic?''



``Way I understand it, she needs to have a tinker in her sphere of influence to borrow their schematics, or a specific device, if she wants to copy it.  Thinkers, too, I think she borrows their perception powers as long as she's tapped into them.  Might be why she's attached to me.  Either way, she didn't have schematics or anything she'd need to modify the guns.''



``Or she \emph{can} modify them, and it's a card she's been keeping up her sleeve for the last while.  I mean, it was only three years ago or whatever that she really showed off her ability to copy a tinker's work wholesale.''



Tattletale nodded.  She frowned.  ``I don't like being in the dark.  But that's the gist of it.  She made cosmetic changes because she couldn't make concrete ones.''



``Well, it's unnerving to think about, but anything about the Simurgh is,'' I commented.  ``When I asked about the aesthetics, though, I wasn't asking about the why so much as the\ldots''



``So much as the \emph{why}?''  Tattletale asked, emphasizing the word.



``Yeah,'' I said, lamely.  ``Why does she \emph{care}?''



``Why does she have feathers and wings?  For all intents and purposes, she could be a crystal that floats here and there.  The end result is pretty much the same.  A few less weapons.  Behemoth?  I mean, you saw what he was, when we reduced him to a bare skeleton.  All the extra flesh, it's decorative.  He doesn't really \emph{need} any particular parts, except legs to move around.''



``It's there to dress them up so they make better terror weapons,'' I said.



``Basically,'' Tattletale said.



``That's not a good omen,'' I said.  ``Because Scion doesn't feel fear.  I'm pretty sure.''



``Maybe he doesn't, and this is a little embellishment for \emph{our} sake, for when she turns on us,'' Tattletale said.



``Can you not spell that out when she's standing twenty feet away?'' I asked.  My pulse picked up a little at the idea, my heart kicking a little in my chest as it switched to a different gear.



``She knows we're thinking it,'' Tattletale said.  ``And she knows there's another explanation we could make.  Maybe it's a clue.  A hint.''



``About what?'' I asked.  ``About Scion?''



``About Scion,'' she said.



\emph{A hint that he can feel fear?}  It didn't ring true, but I preferred it to the alternative.



``Let's go through and\ldots'' I said.  I couldn't bring myself to say I \emph{hoped}.  ``\ldotsMaybe the Simurgh can make her way through the portal, and maybe we'll find out.''



``Yep,'' Tattletale said, smiling a little.  She probably knew the reasoning behind my word choice.



For that matter, it was very possible the Simurgh did too.



Which left me with the question of why I'd even bothered.



\emph{Going through}, I thought.  \emph{Hopefully there's people on the other side that can't read me like a book.}



My phone lit up as a connection was established to a satellite.



A moment later, the connection was secured.



The clock changed, followed by a time zone and a symbol.  \emph{Four forty-six, Eastern standard time, Earth Bet}.



I stared at the world that stretched out before us, and it was \emph{wrong}.  Perspective was skewed.  Lines bent where they should have been straight, and the expanse to our left was somehow more extensive than the space to our right.



The horizon should have been straight, or at least a gentle curve to accomodate the planet's natural curvature, but it was almost a wavy line.



``The fuck?'' I muttered.



``Vista,'' Tattletale said, very matter-of-factly.



The Simurgh reached the portal.  I was reminded of Leviathan breaking into the shelter beneath the library as I saw her put one hand on each side of the portal.  She wasn't quite as large as he was, until you added up the wings and wingspan.  Put all the wings together, and her mass was probably equivalent to her older brother's.



She passed through with little effort, dropping almost to her knees to get her head through.  The wings followed, each wing stretched all the way behind her.  The feathers rasped against the boundaries of the portal as she floated forward.



The outer edges wavered a fraction, as if the stress threatened to bring the portal down entirely.



Then she was through.  She flexed her wings, then folded them around herself.  The halo came through in pieces.



``That answers that,'' Tattletale said.  She added a very unenthusiastic, ``Yay.''



The Dragonfly made its way to us, stopping no less than four times.  With each stop, it descended to the ground and refused all incoming commands.  A minute would pass, and then it would take off again.



It took me a bit to realize \emph{why}.



Vista.  The autopilot didn't seem to like her power.



``Just how much area is she manipulating?'' I asked.



``She was only ever held back by the Manton effect,'' Tattletale said.  ``Number of people in the area.''



``And there's not many people left in Bet,'' I spoke my thoughts aloud, as I made the connection.



``Consider it a bonus,'' Tattletale said, raising her head as the Dragonfly came into view, ``In a sad, not-really-a-bonus sort of way.  Empty earth makes for a convenient battleground.  If we're able to fight here, that is.''



The Dragonfly set down, the ramp opening before it was even on terra firma.



It took a minute to plot out the route the Dragonfly should take, looking at what the cameras had tracked, seeing where the distortions were.



``Something's \emph{really} wrong,'' Tattletale said.



``With the distortions?''



``The distortions are a band-aid.  Vista's trying to fix something that's gotten fucked up,'' she said.  ``How do you plot the course?''



I mapped out a course to take us to the Gimel portal.



Tattletale changed the course, adjusting it to match the distortions we'd mapped and some we hadn't.



It took several minutes, all in all, but the resulting trip was fast.  The Dragonfly's onboard system kept trying to calculating the remaining time for the trip based on our location, only to get tripped up by the folded and pinched space.



Then we hit Silkroad's power, and accelerated to nearly three times the speed.  Tattletale was caught off guard, standing beside my chair, and fell, dropping her laptop onto the hard floor.



Both the distortion and Silkroad's power stopped when we were a distance from the portal.  The effect was disorienting.



Corridors of folded space with the dim pink corridors of Silkroad's power stretched out in every direction.  Connecting points.



Towers surrounded Brockton Bay, set on mountaintops and high ground within the city itself.  It necessitated a careful approach.  As we passed between two, I saw that they were communication towers, crafted to put satellite dishes at high points rather than provide shelter.



The craft settled down, and we climbed out.  They'd finished the ramp leading up to the portal, and it was easy enough to make our way up.  I opted to walk beside Tattletale instead of use up my jetpack's fuel.



Twelve percent capacity remaining.  An hour or two of flight.



Vista stood at the top of the platform, on our side of the portal.  A Chinese woman in an elaborate Sari-style dress stood beside her, as did a man I recognized as the Knave of Hearts from the Suits.  Others were nearby, but seemed less like part of the group and more like bystanders.  Kid Win was sitting at the edge of the platform, tools and a gun in his lap, abandoned as he stared at the Simurgh.



The Knave of Hearts muttered something in what I was guessing was Dutch.  Louder, he commented, ``They weren't joking.''



``What happened?''  I asked, the second we had their attention.



``Cauldron's running with their tail between their legs,'' Vista said.  ``Big promises, excuses about having all the power and being the only ones who can really put the screws to Scion, and then they run at the last minute.''



``Let us not be hasty,'' the Knave of Hearts said.  ``It is possible Scion hit their headquarters.  We won't know until we have more information.''



``We can't \emph{get }information,'' Vista said.  ``Because they never gave us a better way of getting in contact, and they never told us where their headquarters are.''



``Yes,'' Knave said.  He looked at me.  ``We have no portals but the ones that were left open.  We cannot communicate by opening a door and talking to the other person.  Vista, Silk Road and I are attempting to patch together an answer.''



``A workaround,'' Vista said.



``Fast transportation between key areas,'' Tattletale observed.  ``Your power and Silk Road's to make the corridors\ldots''



``I am handling communication and pinpointing the other portal locations,'' Knave said.  ``The Hearts of the Suits have good relations with other teams and places.''



``I can give you the coordinates,'' Tattletale said.



``We have the coordinates,'' Knave said, sounding annoyed.  ``All but the concealed portals.''



``I think I know where those are,'' Tattletale said.



Knave looked even more annoyed at that, but he nodded.  ``Step through, talk to the guys at the station, they'll get you set up.  We'll handle the ones we know about while we wait.''



The station was on the other side of the portal.  A way to keep the civilians from trying to go back to Bet to loot and getting themselves killed or stranded, and a place where they could organize things.



Tattletale and I both gave up our phones.  The technicians on the other end changed settings to bring them on board with the hodgepodge arrays they'd put up on both Bet and Gimel.



Tattletale reclaimed her phone, then paged through the contents, checking settings.  When she was satisfied, she looked at me.  ``I don't expect you to hang around while I'm doing the geek thing and pointing those guys to the right places.''



I nodded.  ``I'll see how the others are doing and get back to you.''



Getting the Endbringers on board had marked the point we'd stopped reeling and started preparing again.  I could see the results.  The Gimel settlement was swiftly transforming from a sprawling refugee camp to a standing ground.  Refugees were being escorted or transported to other locations, packing up tents and possessions and climbing into trucks and helicopters.  It made room for the capes that were here.



Miss Militia was at the center of it, giving orders, managing the capes and the civilians in charge.



Squads were organized, many from the Protectorate, not in rank and file, but clustering according to their respective teams or organization.  Here and there, they'd gathered in more specialized groups.



I could see Rachel, Imp, Foil and Parian with the Chicago Wards, sitting or lying on the closed bins that held supplies for the settlement.  Only Golem was absent.



I felt a moment's trepidation.  I had doubts, regrets, even a kind of shame, when it came to the Chicago teams.



I'd said it out loud, but I'd never really \emph{faced} the decision I'd made: giving up on being a hero.



Still, I found myself walking up to them.



``Here she is,'' Grace said.  ``Make your way here okay, Weaver?''



``Doormaker left a door open for us,'' I said.



``He left doors open for everyone,'' Tecton said.  ``But navigation's a little tricky.  Can't always make it from point A to point B.''



``We did okay,'' I said.  ``Vista was saying this is a cut and run on Cauldron's part, but I can't imagine this as something malicious or cowardly.  They wouldn't have left the portals here if it was.''



``I agree,'' Tecton said.



``Who's looking into it?'' I asked.



``Satyr and the other ex-Vegas capes,'' Grace replied.



``Isn't that like sending the fucking fox to guard the henhouse?'' Romp asked.  ``Except it's sending the confusing mind-game head-fuckers to answer the confusing, fucked-up riddle?''



``\emph{Yes},'' Imp said.  ``\emph{Totally}.  God, it's nice to finally have someone who can explain situations clearly.''



``More like,'' Foil said, ``sending a group that's very well versed in conspiracy and subterfuge to deal with the sort of thing they're very good at handling.''



``Now you're being confusing,'' Imp said.



``Where's Tattletale?'' Rachel asked.



``Outside.  Helping Vista and Silk Road to put together new rapid-travel routes.''



``Okay,'' she said.



``Do you \emph{miss} her?'' Imp asked, turning around.  ``Like, actually?''



``She's a member of the team.''



``But you miss her!  That's awesome!''



``I don't,'' Rachel said.  Then, after a moment's thought, she added, ``And that means it isn't awesome.''



``I thought you couldn't stand her.''



``I can stand her, and it took a long time to get that far.  That's all it is,'' Rachel said.



``But you \emph{asked}.  Like, for the first time ever.''



``I have a question for her.  That's all.''



Romp looked at her teammates, turning to Grace, then Tecton.  ``Am I the only one who hears these guys talk and wonders how the fuck they ever got to be in charge of a city?''



``Don't fucking swear,'' Grace said, saying the line as if it were reflexive by now.  Romp looked annoyed, but Cuff smiled, and I could see Tecton looking away, as if he was forgetting that people couldn't see his face while he had the helmet on.  I, too, smiled.  Romp was completely unware about \emph{why} it was funny that Grace was admonishing her on the swearing.



I turned to Rachel, ``What's the question?  Something I can help with?''



She shrugged.  ``This dork with Miss Militia was telling me some tinker was wanting to try something with my power.  Give my dog some drug shit a rat made?  I didn't follow, and he kept talking to me like I have brain damage, which I don't, so I didn't listen.''



``Which made the guy step it up even more,'' Imp commented.  ``Until it sounded like he was talking to a five year old.''



``I walked away,'' Rachel said.



``Stuff a rat made?'' I asked.



``Lab Rat,'' Imp said.



``Wouldn't work,'' I said.  ``Her power burns up toxins and chemicals in the dog's systems.''



``I said that when they said they wanted to use drugs,'' Rachel said.



``They know that already,'' Imp said.  ``They wanted to try anyways.  Have some things left over from the previous fight.



Dosing mutated dogs with Lab Rat's leftover transformation serums?



Would the gains be additive?



``The drugs they're talking about are the only reason I'm still here,'' I said.  ``Honestly, I'm seeing only two outcomes.  Three, maybe: the effects stack up and Rachel's dog gets even tougher or more versatile; the dog ceases to be a dog while the serum's active and Rachel's power stops working; or it's made for humans and not dogs, and we get a negative reaction.''



``Two out of three odds,'' Romp said.



``Actually,'' Tecton said, ``Nothing's guaranteeing that the odds of any result are even.  Could be a ten percent chance of the first, five percent chance of the second and an eighty-five percent chance of the last one.''



``And a five percent chance it's something else entirely,'' Imp said, sagely.



Tecton shook his head.  ``That doesn't add up.''



``Ignore her,'' Parian said.



``The numbers don't mean anything to me,'' Rachel said.  She frowned, making eye contact with me.  ``You think I should?''



``I do.  Anything and everything we can think of to mix things up or combine powers is good.  I \emph{really} like that there are people out there thinking outside the box.  It's exactly what we need right now.''



``Right,'' Rachel said.  She hopped down from the lid of the supply container.  ``Going to go talk to her then.  If that guy tries baby-talking to me again, I'm going to make Bastard bite him.''



``No way.  You gotta fuck with his head,'' Imp said.



``Biting people is more satisfying,'' Rachel responded.



``No, look\ldots uh\ldots Tecton.  You gotta give me something really smart and scientific sounding.  Like, say what Taylor said, but in smart-guy words.''



``Critical mistake here: you're implying Tecton is smart,'' Romp said.



Tecton sat up straighter.  ``Hey.  Just because I'm not your team leader anymore--''



``--You're totally not the one who gets to order me around,'' Romp replied.  ``Deal with it.''



``Run a lap,'' Grace said, her voice quiet.



Romp turned around, eyebrows raised.



``A lap?''



``\emph{Two }laps,'' Grace said, her voice quiet, cold and dangerous.  ``For not moving the second I gave the order.''



``What am I supposed to fucking run around?''



``\emph{Three} laps for swearing, \emph{four} because you're still here.  We can do five if you don't move \emph{now}.  Start running, and if you don't pick a big enough area to run around, I can give you another few laps.''



``This is \emph{balls},'' Romp said, hopping down from the bin's lid.



``Five laps, then,''  Grace said.



``I \emph{know} I'm getting more laps by talking, but I needed to state the truth for the record.''  She kept talking, speaking with each footfall.  ``\emph{Balls, balls, balls}.''



The moment she was out of earshot, Grace and the others broke into laughter.  Foil was the only member of the Undersiders who seemed to get it, her shoulders shaking in silent laughter.



``I can't believe she actually went,'' Cuff said.



``Don't let her exhaust herself,'' Tecton said.



Grace shook her head, still smiling.  ``I'll stop her after she finishes the first lap.''



``Okay, I need something to write on,''  Imp said.  ``Anyone?''



``Here,'' I said, getting a notepad from my belt.  I handed it to her.  ``Why?''



She handed the notepad to Tecton.  ``So Tecton can write something down.  And I hold it up, like a cue card, and Rachel recites it, sounding like a genius, and we blow dr. baby-talk's mind.  And if he turns around, I use my power, so he's never the wiser.''



Tecton nodded, ``I can do that.''



I winced.  ``There's a flaw in that.''



``It's brilliant,'' Imp said.  She looked around, turning to Parian and Foil.



Parian only extended a hand towards Rachel.



``What?'' Imp asked.



Parian gestured again, pointing.



``I don't get it\ldots Rachel\ldots oh.''



``I don't read much,'' Rachel said, blunt.



``Annnd now I feel like a dick,'' Imp said.



``I don't care,'' Rachel said.



\emph{She probably doesn't}.



``That doesn't make me any less of a dick.  How often do I get reminders about the reading thing?''



``It doesn't matter,'' Rachel said.  She looked annoyed.  ``This is why I don't talk to people.  Why are we still talking about this?''



She was more irritated at the fact that Imp wasn't dropping it than the fact that her illiteracy had been brought up.



``Maybe if I come with?'' Tecton offered.  ``I'll distract whoever Dr. baby-talk is, and you can talk to Miss Militia about dosing your dogs.''



``Or you can tell me what you were going to write down and I memorize it,'' Rachel said.



A few people in the group exchanged glances.



``Really simple solution,'' Rachel said.  Except now she was talking to \emph{us} like \emph{we} were the idiots.



``I'm not sure \emph{I} could memorize it,'' Tecton confessed.



``The kid that's running the lap said you weren't that smart,'' Rachel answered.  ``Try me.''



``Okay, uh.  `I see three possible outcomes'\ldots''



Rachel repeated what he'd said.



They continued, Imp leaning forward and kicking her legs where they dangled from the edge of the bin.



Grace interrupted my observations.  ``You're wearing black.''



I felt a bit of guilt welling.  No, guilt wasn't the right word.  I was at peace with my decision.



I just felt a little ashamed that I hadn't been more upfront about it, with the people I'd spent years working with.



``Yeah.''



``I suppose you're not going to get around to having that meeting with the PRT guys, getting yourself moved up from the Wards to the Protectorate?  Unless I'm reading too much into the costume choice.''



``You're not,'' I said.  ``No, I suppose I'm not going to have that meeting.''



``Is it that we failed with the Jack thing?''



``That's not the entirety of it,'' I said.



``But it's part of it, right?  Isn't that unfair?  We had, like, a four percent chance of success going in, and we didn't stop it from coming to pass, so you bail?''



``I said it's only part of it,'' I repeated myself.



``I \emph{know},'' she said.  I could see Tecton and Rachel pause, catching something in Grace's tone.



When Grace and I remained silent, they resumed.  ``\ldotsthe cross species interactions\ldots''



``\ldotsthe cross species interactions.''



``I know,'' Grace said, after a pause.  ``I get that.  I get that there's other reasons.  Like the fact that you love those guys and you never loved us.  Cool.  Makes sense.''



``I \emph{liked} you guys.''



``But you didn't love us.''



``No,'' I said.



``I get all that.  But Golem's pulling away too, and I \emph{know} that's because that we had only that fucking four percent chance and we failed.  So I draw a connection, think maybe you're more bothered about that than you let on.''



I looked at Cuff, who was watching me intently.  She looked even more intent and focused than Grace did.



Then again, she was a little more invested in how Golem was doing than most.



``Yeah,'' I said.  ``Probably.''



``It's shitty,'' she said.  ``Both Golem and you, drifting away.''



``I know, and it \emph{feels} shitty,'' I said.



``Then that's consolation enough, for me,'' Grace said.  She relaxed a little, then glanced at Cuff.



``I'm not really the type to nurse grudges,'' Cuff said.  ``I just want Golem thinking straight again.  He took it hard.  So you'll get my forgiveness if you go talk to him.''



``I think that's something I can do,'' I answered her.



She smiled.  ``He's at the phone bank, near the station, if you want to find him.''



\emph{Now}?



But Cuff was smiling, looking so \emph{intent}.



Weaponized\emph{ niceness}.



``Right,'' I said.  I turned to go.



And I could see people moving, running.



I felt a pit swell in my stomach.



``No,'' Imp said, following my line of sight.  She could see squads getting into formation.  In the distance, the aircraft that had been moving refugees were turning around, coming back to us.  ``No, no.  We had such a good joke going, don't you \emph{dare} ruin it.''



Romp returned to us, breaking into a run to close the remainder of the distance.  ``Someone's saying he's hitting Samech.  It's one of the Earths Cauldron was going to watch over.  There's only Dragon, the Guild and some Protectorate guys there.''



``Let's move,'' I said.  ``Through the portal.  We'll use the Dragonfly.  Faster than waiting for another ship.  Rachel, look for doctor baby-talk, if we can grab something from him before we leave, great, but let's not dawdle.''



There were nods all around.



I could see the other heroes.  Miss Militia and Glaistig Uaine.  Revel and Exalt.  Protectorate teams, sub-teams of the Suits, including the non-combat teams of the Hearts and Cups.



People hurried to organize, pulling on costume pieces they'd left off and checking weapons, clearing out of the open spaces where shadows grew as the aircraft descended.



One by one, the ships began to take off, flying through the tall, narrow portal.



Three ships, then four.



But the fifth didn't take off.  I reached out with my swarm, trying to catch what people were talking about, to make sense of the situation, but everyone important was already on a ship.



King of Hearts was the only person of any meaningful rank who spoke the same language I did and who wasn't mobilizing to \emph{leave}.  The leader of the Meisters, \emph{Vornehm}, was giving orders in German.  A scary-looking Master class cape with an army of clay men carrying tinker weapons was ordering other people around with the same harsh voice he was commanding his own troops.



But there was no explanation of why more ships weren't taking off.



Had the fight already ended?



``Keep moving,'' I said, ordering the teams forward.  \emph{Tattletale will know}.



As confusion descended, people started falling back into their previous state, gathering in clusters of familiar people.  It almost seemed like we were the only group with direction, pushing against a milling crowd.  We weren't, but the illusion was there.



And that same effect made it possible to see when the crowd \emph{did} find direction, a common, mutual interest.  Heads turned, chins raised.  People found postures where their feet were set apart, as if ready to move at a moment's notice.



Scion.  Here.  Floating above the bay like he'd floated above the ocean in his first appearance.



\emph{He's targeting us}, I realized.  Two of our organized settlements in as many minutes?



His hands hung at his sides.  The golden light that radiated from him cleaned his clothes and hair, but there was enough blood on his costume that the light wasn't rendering it as pristine as it should.  His eye sockets were dark, with the way his forehead blocked the sun's light.  That same sunlight made the edges of his hair and body glow with the light that wasn't completely blocked.



He didn't even raise his hand before he fired.  Lights no bigger than basketballs streaked forward, leaving trails glittering behind them.



Two of Dragon's ships detonated violently.  Occupants dead or grievously injured, people in the area of the craft wounded by the fallout.



By the time I'd turned my head to see his follow-up, Scion had closed the distance, moving right into our midst.



Capes with reflexes better than mine were already reacting, throwing a multitude of effects in his way.  He plunged through the defenses like they weren't even there.



\emph{Something} got in his way, but he flew around it without a second thought.  He stopped right in front of a cape.  Quite possibly the cape that had stalled him momentarily.  A dark-skinned man in gray.



A swirling gray effect swelled between him and the target.  He struck it with a glowing hand, and the effect distorted, growing thin.  Another strike, and the effect dissipated.



Other capes were hurling effects at him.  Most glanced off.



He caught his target around the throat.  Didn't squeeze.



But the golden light began to eat into the target's body and costume.  Scion let the man drop.



Not a scream.  Only twitching, frantic thrashing as the golden light continued to consume.



Foil raised her arbalest.  I could see our entire group tense as she raised it, Parian's hands going to her mouth.



A moment later, Parian's cloth was unfurling from behind her back.  Rachel was making her dogs grow, while Cuff was manipulating a shotput into a blade like the one from a circular saw.



For my part, I began drawing the bugs into decoys, sending them into the air.



Oblivious to it all, Foil took aim, then ran her hand along the bolt she'd loaded in place.



I could see her draw in a breath.  I'd taken marksmanship classes.  \emph{Squeeze the trigger as you exhale.}



The shot flew through the air.



Scion wheeled around and caught it.



It wasn't just his costume, I could see.  All the lines of his body, his hands, lines that made it so he didn't look wholly artificial, they were filled with the detritus of smoke and blood and other grit, and the golden light had only washed the surface clean.  The deepest cracks held the remainder.  It made fine lines look more like crags.



I was almost glad that it took away from his human appearance.



He let the arbalest's bolt drop to the ground.



His eyes were on Foil.



A golden light swelled in his hand.



We spread out, but Foil didn't even flinch.  Even as Cuff backed away, Foil reached out to touch the sawblade, imbuing it with power.



Scion reached out, and Parian used her power, encircling Foil with the end of a length of cloth.  Not an animal, only an arm.



In the instant Scion loosed the bolt of light, Parian flung Foil away.  Not a simple throw, but a reckless, inhumanly strong one.



Foil was removed from the battle.  Sent beyond what would have been the outskirts of the city, if we were in Bet, cast out in the direction of the Bay itself, until she was only a speck.



The bolt hit ground, fifty or sixty feet behind us.  Other people died instead.  People I didn't know.



No longer interested in Foil, Scion turned to the nearest cape, lunging.



Cuff threw her circular blade.  Without even looking, Scion batted it aside, striking an unaffected part towards the middle.  His attention was on a cape, and he swiped a glowing hand through the cape's abdomen.



What didn't burn spilled forth.  His screams were joined by that of a friend, another cape who screamed in horror over what had happened to him.  Scion very deliberately walked past this other cape to attack someone else.



Picking us off, choosing targets.



Maximizing pain and suffering over raw destruction.



\emph{Experimenting.}



And there was precious little we could do about it.



Precious little \emph{I} could do about it.  My bugs formed into more decoys.  Other bugs searched for the key players.  Where was the man Rachel had described?  The one with the serums?  Where was Miss Milita?



The Simurgh was passing through the portal, and people who'd been trying to flee to Earth Bet were now scattering, trying to flee both the Endbringer and Scion at the same time.



Horribly timed, as entrances went.  Our best hope was that he'd \emph{keep} toying with us, that enough time would pass that capes stationed at the other major portals could use the fast-travel routes to get to us.



Something like an Endbringer was all too likely to change his mind.



\emph{It's the beginning of the end}.





