





Oh, how small we were, in the grand scheme of it all.



Our planet was but a speck in the midst of the milky way galaxy, which was a speck in the midst of the known universe.  We were fighting to save it, and yet it could disappear without anyone in the nearest solar system even noticing.



Small, insignificant.  Little more than ants before a giant.



A pencil-thin beam lanced out from his fingertips.  A sweep of his hand, waist-level, and it cut through the crowd.  Cut through thighs, knees, calves, feet.



Swept towards \emph{us}.



No time to act, to save anyone.  Only to get out of the way.  I jumped, activating the flight pack.  I looked to my teammates, my breath trapped in my throat as I waited to see who was hit.



Parian still had the `stuffed' arm connected to a nearby building.  A sweep of the arm caught a solid twenty people, catching them in the bend of the cloth and lifting them off the ground as the beam passed by.  Rachel, mounted, wasn't so lucky.  The beam caught three of the dog's legs.



Rachel fell, tumbling to the ground.  The people Parian had tossed aside, Parian included, fell in heaps, landing awkwardly.



But alive, all but one of them untouched.



In the chaos that followed, I could see the blood.  This wasn't a beam that seared, like some lasers did, and it didn't cauterize as it cut.  It disintegrated, leaving arteries free to pump blood out onto the grass and dirt.



A number were laying there in shock, but there were some who were fighting, even as they bled out.  Scion was momentarily caught up in a storm of shards that seemed to give him pause.



The Suits were among the injured, and King of Cups was patching up the damage.  Limbs were replaced with pitch black simulacrums that caught the light in odd ways that only highlighted the very edges.



I saw Lung among the artificial limb recipients.  He'd stayed in Brockton Bay in the company of Miss Militia while the rest of us had said goodbyes and made arrangements, so it wasn't puzzling that he was here.  No, the confusing bit was that the fight had only been going for two or so minutes, and he was already transformed halfway to the state he'd been in when the Undersiders had first rescued me on the rooftop.  Transforming five or ten times as fast?



He'd been in the company of Panacea\ldots had she done something?



Canary had said Lung had avoided picking fights during his stay in the Birdcage, relying only on his reputation.  Maybe this was a one-shot deal.



It didn't take the capes King of Cups had healed very long to get their bearings, scrambling to get away, or backing away as they used their abilities.  A cape with deep black skin and an overly tall white helmet was sliding groups around like a chess player slid a piece into position.  Another cape, just beside him, was altering the battlefield, getting obstacles out of the way.  The ground swallowed walls, supplies and vehicles like it was suddenly water, rippling as they dropped beneath the surface, then changing, becoming solid once more.



Cover didn't work as a concept, I supposed, when his attacks cut through it so easily.  Still, I wasn't sure it was the brightest move.  There had to be a more optimal way of rearranging the battlefield.  Putting some people on higher ground and some on lower, without limiting their ability to dodge.



A glance over my shoulder showed the Simurgh standing by the portal, wings folded so the ends were aimed at Scion.  She had reconfigured her halo, and every single one of the guns were pointed in the same direction.



But she didn't shoot.  She waited.



My swarm-decoys massed in the air around Scion, some dividing into further copies.  He continued to ignore them, targeting specific capes.  A sphere of light was tossed in Glaistig Uaine's direction.  She didn't move or fight back.  Instead, she was saved by the guy with the tall helmet, shifted out of the way.  \emph{Bishop, Chessmaster, Curling-guy?}



Unruffled, she called three spirits forth, then took flight, positioning herself high in the sky, entirely out of the fight.



\emph{Running}?



Scion attacked again, picking different targets.  King of Cups created more phantom limbs, an array of twelve or so arms of varying size that spread out from his shoulders, and caught a teammate's hand.  He was pulled out of the way, but the sphere swerved in the air, drifting his way.  It crashed into one of his shoulders, and dashed the arms to smithereens.



King of Cups tumbled, then used his power to patch up the damage.



I wasn't sure how that worked.  The lines of pain on his face seemed to ease as his power replaced the injured parts.  Was there some sort of interaction there?  A connection of nerves, arteries and veins?



Queen of Swords had a shortsword in hand, stepping forward as if to shield King of Cups with her own body.  Her sword seemed more ceremonial than useful.  I'd seen capes that used props to focus their powers, and she appeared to be one of them.  As she swung the sword, lines of light were cast out around her, connecting to various capes in the crowd.



Chaos, really.  So much going on, so many capes, all trying to focus on a single target.  A sphere of darkness made contact with series of ribbons that spiraled around one another, and they were both consumed in a spiral of intermingled effects well before reaching Scion.



Someone was taking my cue, filling the sky with what looked like stone statues of capes, stiff with arms at their sides.  The battlefield, the crowd, the sky, it was impossible to keep track of it all.  Even if I sacrificed decoys, I still had to \emph{think} about what was going on.  I'd be able to sense that bugs were dying here, that something was moving from one point to the next, but I wouldn't necessarily know who was doing what.  What did the ribbons do?  What was Queen of Swords doing with her power, connecting capes?



Worst of all, for everything we were doing, Scion wasn't reacting.  He wasn't getting seriously hurt, and he wasn't taking any of the bait.



I dropped out of the sky, landing beside Rachel with a little more force than was maybe smart.  Conserved fuel, and got me out of Scion's line of sight, but I felt a twang in my new right leg that suggested maybe it wasn't as flexible as it should have been.



``He's bleeding out,'' Rachel said.



It was Bastard, wounded, three of his massive legs severed, blood forming a ridiculously large puddle beneath us.



``He's safe inside, isn't he?  The smaller, real version of Bastard?''



``Same blood in both of them.  The outside won't fall apart before he loses too much blood,'' she said.  ``I think.''



``Then leave him,'' I said.  ``Go look for babytalk.  Get one of the Lab Rat doses, bring it back.''



I could see the stress on her expression.



``Go,'' I said.  ``I'll look after him.''



Rachel bolted.  I turned, saw a cape lying on the ground with her eyes open, staring at the sky.



Paradoxical, stupid, selfish, arrogant, and short-sighted, to even think about giving my attention to a dog -to a wolf- before trying to revive the woman.  Still, I took my knife to her cloak and wadded it up to stop the blood loss.  When I couldn't cover enough space with my hands, I used my body to press it against the site of the injury.



I told myself she was beyond saving, that other injured capes were being helped by King of Cups, and that Bastard wasn't getting the same treatment, that he wouldn't.



But the reality was that I'd cast aside the strict ideas of right and wrong, that I'd told myself I'd be \emph{Taylor} instead of Weaver or Skitter, and this was what \emph{I} wanted to do.



Because \emph{I} was a hypocrite, I was selfish, arrogant, short-sighted and even stupid at times.  Because I could only face this situation with what I knew, and I knew that Bitch wouldn't fight any further if we just let Bastard die, and if our team started falling apart, I wouldn't know what to do at \emph{all}.



Lung limped forward, not to fight Scion, but to shout something.  His voice was nearly drowned out in the noise.  Not entirely, it was too loud to be \emph{entirely} masked, but nearly. ``\emph{Remove it}.''



I didn't follow his meaning until bugs moved past his legs, touching the hard surface of the artificial leg.  Unchanged, unaltered by his power.  His regular leg was almost a foot longer.



The tall-helm cape slid some of the Suits out of the way.  They started shouting, asking to be moved back.  He responded in French.



Disorganization, a lack of coherency.  A lack of organization.  I clenched my jaw and did what I could to stop the blood from welling out of the stumps of Bastard's legs.



This wasn't a monster that was four or five stories tall.  It was a single individual in a crowd, with capes using powers that would inevitably cause more harm to any bystander they accidentally struck than they could possibly deal to the intended target.



Queen of Swords touched the tip of her sword to one of the main lines of the diagram she'd created.  A circular blob expanded from the point like blood welling from a prick from the blade, two-dimensional, dark blue and translucent.



She drew a gun from her hip with her free hand, aimed it at the blob and fired.



The bullet hit the blob and pushed against it, slowing down with every fraction of an inch it traveled.  It came to a complete stop, the previously flat surface of the blob-portal-thing now more of a cone, poked out of shape by the bullet's movement.  For a half-second, I thought it would be like a trampoline, sending the bullet back to sender.



Then it punched through, and I could see ribbons, fire, darkness and innumerable other effects trailing behind it as it resumed normal speed.



It struck Scion as he started to fire another beam of light at the crowd opposite me and the Undersiders.  Scion stumbled, the aftermath of a dozen different powers rippling over, around and through him, and the beam was cut off by one of the powers.



She began changing the map, breaking some connections, expanding others.



Scion turned her way.



It was just the right moment for our first reinforcements to arrive.  Distorted terrain marked Vista's arrival, as she folded the earth around Scion, surrounding him with walls of earth.



I looked to see, and saw her and Kid Win standing on a twelve-foot high bulge of earth.  Kid Win was getting himself set up, hunkering down, while Vista stood at a point slightly above him.



Tattletale was with them.  Hanging back, as if using Kid Win as a shield, her eyes on the battlefield, a phone in hand.  Most likely to relay information.



Others were filing between the Simurgh's legs.  Gavel, now clean-cut, his once-shaggy beard now cut to a style that would have been ludicrous if he didn't have the reputation to back it up; two perfectly straight lines that met at a sharp 90-degree point at the chin.  His hair had been buzzed, flat at the top.  His mask covered only his forehead, eyes and nose, his lips were set a firm line.  He wore a skintight black shirt without sleeves and heavy canvas pants, with boots that looked like they could be used to crush stone.



His hammer, by contrast, was solid steel, with sharp lines that seemed to parallel the clean lines of his hair and beard, a pole that seemed too big to wrap one's hands around.  The entire thing was as big as he was, probably three or four times the weight.



And he was \emph{big}.  Bodybuilder big, broad-shouldered in a way that you rarely saw, even in movies.



Crane the Harmonious was just behind Gavel, joined by three capes I assumed were her disciples.  Two of them looked like they were ready to enter a battle, ducking low, moving like trained soldiers entering a battlefield.  A third looked like a scared kid.  Reasonable, something to be expected from people who were walking into a situation like this.  Crane, for her part, walked with her hands clasped behind her back, chin up, like she was completely oblivious to what was going on.



Scion broke through the wall of hard rock, and it seemed to actually take a modicum of effort.  He directed an attack at Vista, Kid Win and Tattletale.  A sphere, just like the one that had totaled the Dragonfly.



Gavel threw the hammer into the air, and it blocked the shot.  The resulting explosion knocked a dozen capes off their feet, struck some of Kid Win's airborne guns out of the air and very nearly knocked Tattletale from her perch.  Crane's disciples were bowled over, but Crane managed to turn with the shockwave, only taking a step back, remaining upright.



The hammer descended, unaffected by the explosion, and Gavel caught the handle in his two hands.



Scion turned his attention to Gavel, throwing one more sphere.



Another detonation.  Capes in the area were scrambling to get away from Scion's new designated target.



Gavel had stopped.  He swayed, then swung his hammer around, striking it against the ground before gripping the pole, as if he'd only needed something to lean against.  His skin was a little darker where it had been scorched, and golden light danced around the edges of the wounds like the orange at the edges of burned paper, where the paper had burned but not burned \emph{completely}.



I could see the Simurgh move, putting one of her larger wings in front of Kid Win.  Stopping him from firing.



I \emph{really} hoped she was on our side in all of this.  Letting Gavel handle this with only the support from the sidelines seemed feeble at best.



Scion suffered a continual onslaught of powers and projectiles from every direction, and the distraction these shots seemed to give Gavel the chance he needed to find his second wind.  The vigilante and ex-cell-block leader of the Birdcage advanced, picking up speed as he found his stride, dragging his hammer beside him.



Scion used a beam instead, directing it at Gavel.



Which was \emph{interesting}.  Maybe.  A beam was what \emph{I }would have used to deal with Gavel.  His power made it so he could only take so much damage at a time, and reduced the severity of any damage to a set amount.  Shooting him with a hail of bullets would be little different from shooting him with one or two bullets, and any given bullet would only gouge out a teaspoon of flesh.



Excalibur's scabbard.  He could have done so much more with the concept, but he'd gone with a hammer instead of a sword.



I stared, watching as he blocked the worst of the beam with the hammer.   Scion stopped, interrupted as Queen of Swords shot him with another power-infused bullet, then resumed the assault.



A spray of bullets wouldn't do much to Gavel, but a steady \emph{stream} of them could whittle him down.  Blind in the face of the brilliant light, Gavel marched forward.  He moved his damaged hammer out of the way, taking the beam in the face and throat instead.



Amazing, perplexing\ldots and I could only stare, watching Gavel's inhuman tenacity, wondering if Scion was using the beam because it was one of the most convenient and effective tools available to him, or because he intuitively understood Gavel's power.



He was supposed to be the source of powers.  It made sense that he'd know the particulars about them.



It was a scary thought.



Gavel got close enough to reach out and fumble, putting a hand on Scion's face, two fingers finding Scion's eye sockets.



Scion pulled back a little, maintaining the beam as it cut into Gavel.  I could smell something like burning hair.  Clouds of it, choking.



Gavel toppled.



No, he was leveraging his full weight, swinging his hammer like an Olympic hammer-thrower might swing theirs.  Not even a complete rotation, but he struck Scion dead-on.



Scion hit the dirt, was plowed into a furrow fifteen feet long.  He half-climbed to his feet, half-floated, and was struck again.  Another swing of the hammer.



It wasn't \emph{hurting} him, but it was an inconvenience, and that was something good in my books.



I could feel the hot blood seeping through my costume, running over my shoulders and down my front.  My back was already sticky with it.  Probably not good for my flight pack.  Rachel was running through the crowd, shoving anyone that wasn't actively fighting to get them out of her way.



Gavel hit Scion a third time, and the hammer, damaged earlier by the beam, fell to pieces.



For the fourth hit, Gavel used the toe of his boot.



But each hit was dramatically less effective than the last.  Scion reacted to the kick, floating back a little, but it wasn't much at all.



Gavel had once been judge, jury and executioner to criminals in Australia.  He'd announce his intentions publicly, swearing vengeance and listing their crimes, and then he'd go after them.



Generally speaking, he transferred his power from himself to his hammer and from his hammer to his target, conducting invincibility.  His target would fly through the air until they hit something, at which point they would be pulverized.



If he was feeling merciful, or if he didn't want to give them a chance, he simply pulverized them with the swing.



But Scion wasn't pulverized.  The golden man reached out and jammed a hand in the largest wound the beam had created.  A golden light flared, and Gavel disintegrated on the inside.  Flakes of burned flesh traced with bits of golden light flew into the air as either half of Gavel's body hit the ground.



Lung, on the sidelines, was as monstrous as he'd been when he fought Kaiser, Sundancer and I.  But he waited.



We needed time.  Time for Lung.  Time for the Simurgh to find her window of opportunity, time for reinforcements\ldots



Gavel, ruthless vigilante, monster, had bought us a good \emph{minute}.  Maybe two.



Scion targeted Vista, Kid Win and the others.  His target before Gavel had grabbed his attention.



Very formulaic, very steady, picking out targets based on who was posing the biggest threat\ldots or the biggest potential inconvenience, and then eliminating them.  Gavel was out of the picture, so he moved back down to the next on his list.



Vista folded more space, then changed the shape of the hill she'd created.  It wasn't fast enough to get her, Kid Win or Tattletale out of the way of Scion's shot.



The Simurgh protected them with her wing.



\emph{Get out of there}, I thought.



Then I did one better.  I broke up one swarm decoy and moved the bugs in their direction.



The bugs flew too slow.  They couldn't cover that much ground in a matter of seconds.



\emph{Get out of there.  He's going to come after you, and people aren't going to be able to save you every time}.



Scion rose into the air, floating.



\emph{Get out of there.}



Queen of Swords shot him again.



Scion turned, slow, his eyes falling on her.  Ribbons, perhaps the most identifiable projectile, sailed through the air, snagging on him and then fixing in the air, as if the other ends were attached to some invisible tether.  It was one of the Swords doing it.



He floated a bit forward, and the tethers broke, falling apart.



Two projectiles, again.



Softballing us so hard he was almost taking pity.



Rachel approached.  She had a device in hand.  One of the matchboxes, Lab Rat juice on demand.  I shifted position as she leaned over Bastard.



``How?'' she asked.  There was a look in her eyes that suggested she was upset, concerned, worried.  She looked at me, at the amount of blood on and around me, and I could even see a note of \emph{anguish, }hidden behind stern eyes and a mouth that was pressed into a lipless line.



``Turn it around,'' I said.  I couldn't reach it without pulling away from where I was applying pressure.



King of Cups blocked the shots using some of the largest arms.  Gorilla arms with massive clawed hands, fanning out from his shoulders, blocking the shot and serving as walls to shield the teammates beside and behind him.



Scion closed the distance, swept a hand to one side, and dashed all but one or two of the artificial arms to pieces.  He caught King of Cups by the jaw.



But he didn't \emph{hurt} the man.



Instead, taking advantage of the pause where capes with ranged attacks \emph{weren't} firing into the midst of the Suits, Scion held King of Cups in the air, and extended a hand.



Not attacking, but indicating.



The hand swept over the capes in question.



``\emph{How}?'' Rachel said, with a bit more emotion.



I reached up, took her hand and pushed it, with the device, down on Bastard's shoulder.  I turned back to Scion as the high-pitched beeping started.



He watched King of Cups as he moved his hand.  The man's expression, which I couldn't make out, seemed to give Scion the answer he wanted.



With his free hand, Scion flew forward, seizing the Queen of Swords before she could get out of the way.



He bent over, and he pushed the pair to the ground.



When they were pinned, he kept pushing one of them.  I could hear a strangled scream.  He had a grip on Queen of Sword's face, and he was simply pushing her head into the ground.  King of Cup's screams were a different sort; not of pain, but horror.



Capes pelted Scion, grabbed hold of his neck, arms and legs with chains, but failed to affect him.  Vista's power made the earth rise around Scion, but when he didn't react, she returned it to normal, leaving room for others to try.



It wasn't just offensive attempts at rescue, either.



``\ldots{}can't teleport them, blocking my power\ldots''



``\ldots{}make him stop, make him stop\ldots''



``\ldots{}someone?  Anyone!\ldots''



I craned my head, looking.  The Simurgh was still blocking Kid Win, and she wasn't shooting.  Glaistig Uaine was in the sky above, orbited by three spirits I couldn't quite make out.



Foil, still gone.



It might as well have been him, the King and the Queen, all alone, for all it mattered.



He jolted a bit, his shoulders and back dropping an inch or two, as something gave way.



The lines and diagrams Queen of Swords had created disappeared, thinning out, then fading away entirely.



I saw King's legs kick, heard his screams intensify.  There was a new kind of horror in the sound.  He manifested new arms, monstrous ones, insectile ones, bird talons and tentacles, even the occasional indistinct head of an animal, grabbing Scion, trying to tear him away, tear him apart.  Futile, just like all the other measures.  Scion wasn't even visible beneath the effects that surrounded him.



\emph{Pulling the wings off flies}.  \emph{Kicking over anthills}.  As evils went, Scion wasn't much more than a child in maturity.



We weren't much more than bugs to him.



``It's not working,'' Rachel said.



``I- what?'' I asked.



``The dose.''



I tore my eyes away from the scene.  The matchbox was beeping, but it wasn't quite the frantic beep I'd heard when mine was going off.



``The dog's physiology, it might read as too healthy,'' I said.



``He's lost half his blood,'' she said, her expression grim.  ``He's not even moving now.''



``I don't know,'' I said.  ``If we get the vials from inside, maybe we can manually apply it?''



``Mm,'' Rachel grunted.



King of Cup's screams reached a fever pitch.  I turned to look, wincing.



``Hurry,'' I said.  ``I need to get in there.''



``And do what?''



Do what?  I didn't know.



``S-``



All at once, the chaos was replaced by stillness.



It wasn't a typical silence.  Typical silence would have left my ears ringing with the sudden shift from noise to an utter lack thereof.



Wasn't a typical stillness.  If it was, I would have felt my heartbeat.



My senses had been replaced.



I watched as two massive beings made their way through the void.



One was familiar to me, in a dim way I couldn't articulate.



Not that I could \emph{think}, really.  I experienced, I took things in, and I understood it.



They were flesh and they weren't flesh.  Something I couldn't parse, given my frame of reference.  I could understand how they moved, and I knew it was because of the senses I was using, senses that allowed me to be aware of these things, to grasp them in terms of how they slid between realities.



I focused on the familiar one, and compared it to its kin.



It was shucking away fragments of itself, discarding them.  It kept select ones.  Abilities focused on violence, on defense.  On mobility and battle and any number of other things.



It exercised a variety of the fragments.  It was taking over for another role, a role that the partner wasn't fulfilling.



The partner was busy, I noted, sending broadcasts.  Messages, to something distant.



But I couldn't interpret the partner in the same kind of depth I could interpret the more familiar one.



I turned my attention to it.  Saw what it saw.  Images of the future.  I was connected somehow to every part of the being, and I was aware of everything they were aware of.  I had only to look.



It looked for a world.



It found the world it was looking for.



It looked for a particular \emph{variation} of that world, and it found it.



And it looked further.  It viewed itself and its partner on that world.  The possible forms they could take, the end results.



It looked beyond that, to possible rebellions.



In the midst of that, in the middle of a trillion images that passed through my awareness in a single instant, over an indeterminate span of travel and viewing, one scene was acutely familiar.



The entity as a golden man.



Capes littering the surface around him, every single one of them unconscious, dead, bleeding, crushed, or burned.  He was untouched, coated only in their remains, thick blood and other, pulpier substances dripping and dropping from his fingers in strings.



He viewed the scene, as he viewed all of the scenes, through the senses of the fragments that had gone ahead, of fragments that had arrived after he had.  They were embedded in hosts, which meant he viewed things through the eyes of the host, and through the abilities the hosts expressed.



I \emph{willed} for it to continue, to go deeper, to provide more details.  But things moved along.  If anything, my efforts dashed the scene from the ongoing stream of sensory inputs.  Instead, I got a glimpse the futures one step further.  Variations.



Every one of them, futures where the entity had survived.  Futures where the hosts hadn't fought back.  Futures where they \emph{had} fought back and inevitably lost.  He was plotting a course to a particular destination in time and causality, just as he'd plotted a course to Earth.  There were criteria, and in each of the visions, things occurred.



These visions were blocked from any particular attention.  Hidden away by some treatment of the fragments, treatment of the entity's own recollections, so the visions couldn't be used against it.



But I could see the essential elements.



He would live, because he'd given himself enough power.  With the criteria he had set, there was no way for the hosts to win, unless he deviated.  With the granted powers, there was no way for them to do any meaningful harm to him.  The entity could see the permutations, the ways they moved and interacted.  He called on a particular fragment, yet to be released in search of a host, and-



\emph{Familiar.  A familiar presence.}



-he could get an understanding of the hosts, filling in blanks that the future-sight and his own mind couldn't.  See how they moved, how they cooperated, how they didn't cooperate.  He could see the strategies they could possibly employ, the strategies they couldn't.



Again, these were censored, blocked in this three-dimensional, xenosensory, interactive memory.



But he could see, and he knew they would fail, as much by their own hand as by his.  He could see how all paths he had considered led to a fulfillment of his mission, his eventual meeting with his partner, in their other forms.  He could see how he wins in every circumstance where he has to fight.  Countless paths to victory.  He would spend the rest of the journey to this planet in picking one, was already setting things up so that paths to defeat would no longer be possible.



\emph{We lose}.



It was my thought, not the entity's.



The thought stuttered, distorted.  Repeated over and over so fast it seemed to become only a jumble of sounds.



Another repetition, where each syllable seemed to take \emph{days} to form.



I opened my eyes, and I saw the scene from the vision.  Scion standing in the middle of the settlement, blood and brains dripping from his hand.



The two words continued, as if in the background, distorted as I turned my head.



It was one of the capes that had arrived with Crane.  He was doing it, distorting the memory.



Making it so the memory wouldn't fade.



\emph{Let me forget}, I thought.  \emph{I don't want to know this.  Let me be ignorant, fight to the end.}



Scion stood, waiting patiently.  No point tearing us to pieces when we weren't aware enough for it to matter.



I looked at him, and I saw the entity from my memory.  I saw the vast thing he was, and I knew that we were specks to him.  He'd held back when he'd used the beam to slice through legs, when he used mere physical force to crush Queen of Sword's skull.  He'd held back, in a fashion, when he'd obliterated the United Kingdom of Earth Bet.



King of Cups howled wordlessly, using his power, and the phantom limbs started emerging from every surface around us.



My back arched as one thrust itself free from my chest.  A tentacle.



A claw emerged from the ground by my neck.



Every surface in sight, marked with the ebon-black limbs, faces, even the upper bodies of indistinct lifeforms.  Some humanoid, some very \emph{not}.  From horizon to horizon, the landscape turned dark as phantom images peppered it, growing denser with every passing second.



With none of the care of the time that he'd taken with Queen of Swords, Scion crushed King of Cup's skull.



The phantom images crumbled into black ash.



``No,'' Rachel said.  ``Fuck it.  Fuck \emph{him}.''



``Rachel?'' I mumbled.



I turned my head, felt my head swim with the aftermath of the vision, or the memory-retention power, and I saw the matchbox, the contents spilled.  The ground beneath was darker.  Dirt soaked with the fluid.



``Was trying to open it when the vision hit,'' Rachel said.



The Simurgh screamed.  Scion gave her his full attention.



She used her power, parting the sea of fallen, reeling capes with her telekinesis.  Capes between her and Scion were tossed aside, and capes behind Scion were dismissed in the same way.  I could see people bounce off the ground, limbs bending in awkward, painful ways as they landed.



Bugs, to be swatted aside when they got in the way.



Then she fired the guns.  Hers and Kid Win's.



\emph{The shotgun approach.}  Cover as wide an area as possible, cover as many \emph{bases} as possible, in the hopes that \emph{something} hits.



I covered my eyes, turning my head.  When that wasn't enough, I covered my eyes with my arm.



There was little sound, but there was a horrific vibration, something that made me worry my insides were turning to jelly.



When I could see again, Scion was gone.



But he wasn't defeated.  I knew that much.



The Simurgh, moving with a deliberate assurance, began reloading each of the guns.  Extraneous pieces of the halo served as battery packs, as ammunition.



Scion passed through the portal behind her.  As if in slow motion, I could see her folding herself forward, her wings wrapping around her body.  Preparing for the attack that was about to come.



He hit her, and he sent her flying through the crowd.  Capes were turned into bloody smears as she collided with them, and the Simurgh was driven to the very far edge of the settlement, to the beaches at the edge of the bay.  The countless guns were pulverized.



Almost casually, Scion created a beam that speared through the center of the hill Vista had made, and the hill crumbled, the effect collapsing inconsistently, the hill and everyone on it falling violently to the ground below.



``Tattletale,'' I said.



``Go,'' Rachel said.



I looked at her, at Bastard, who barely seemed to be breathing anymore.  In the distance, Scion followed up his attack on the Simurgh.  She continued to focus on defending herself, raising sand in false Simurgh decoys, manipulating water, all to misdirect, as she kept her wings folded around her like a shell.



``Go,'' she said.  ``Help Tattletale.''



There was something in her voice.  Something that suggested she \emph{did} care after all.  Imp's ribbing aside, Rachel did value Tattletale on some level.



I tried to stand, and felt the strength of the congealed blood that bound me to the cloth, which was in turn bound to Bastard's foreleg stumps.  My swarm and a bit of pulling on my part broke the connection.  I stood, and my leg throbbed where I'd dropped a little too quickly to the ground, earlier.  Flight was easier and faster.



I was halfway to Tattletale when I sensed Rachel moving.  Clawing at the dirt with her fingers, cramming it into Bastard's mouth, almost climbing into his mouth as she shoved dirt down his throat.



I sensed him react, choking, making noises far too feeble for such a great beast.  Rachel had to \emph{heave} herself free to avoid being in the way as he reflexively slammed his jaws shut, coughing and hacking.



She grabbed handfuls of the dirt and smeared it on the stumps of his wounds, instead.



Glaistig Uaine deemed it her moment to descend.  I moved bugs to her so I'd know what was going on as I landed, gently, near the ones who'd been on the hill.



Kid Win held Vista, and Tattletale had landed on her back near the portal's base.  Crane and her cronies stood by, impassive.



``My guns didn't do anything,'' Kid Win said.



``You okay?'' I asked Tattletale.



``Mostly.  Soil was soft as I landed, but\ldots still a drop,'' she said.



``You're fine,'' Crane said.  Her tone made it sound like something that would be true if she said it with enough conviction.



``That vision\ldots''  Tattletale said.



``Anything useful?'' I asked.



``If it was useful, he would have censored it,'' she said.



I looked at Crane.  ``Did you plan that?  Why bring that guy?''



``Teacher asked me to bring him,'' she said.  ``\emph{That} is not one of mine.''



\emph{Teacher.}



So many plays.  So many big players.



I felt a welling anger, frustration, a note of hopelessness I hadn't felt before.



Glaistig Uaine had Gavel as a spirit, and was pounding at Scion, with little effect.



``He adapts,'' Tattletale said.  ``I was saying it on the phone.  He just needs a reminder about which passenger we've got, and then he adjusts some internal frequency, and he adapts.  Anything we can throw at him, he knows how to cancel out.''



Glaistig Uaine changed up.  Three spirits.



Eidolon was one of them.



``So we need to beat him with one shot,'' I said.



``Not doable,'' she said.



``Because we aren't hurting him,'' I spoke my thoughts aloud.  \emph{We haven't touched him}.



``We're hurting him,'' she said.  ``Kind of like how people hurt Gavel.  He's\ldots he's got a defense, not making him invincible, but making him a living portal.  So you hurt him, and faster than you can do anything, he just swaps out the damaged material for material from\ldots this bottomless well.''



\emph{A well}?



I could see Lung finding his feet.  As large as Leviathan, four wings, four hands, two digitigrade feet.  King of Cup's power had faded, but regeneration had made up for it.  Lung was intact, naked, massive, monstrous and bristling with layers upon layers of silver scales.



He joined the fray, supporting Glaistig Uaine as she took to the air, flying through the crowd to access the wounded and dying.



I could see Eidolon's shadow briefly take hold of the injured, then toss them aside.  Glaistig Uaine, for her part, accessed the dead.



The other two spirits attacked Scion.  Here and there, attacks made him react.



But, as Tattletale had said, no attack was as effective on subsequent iterations.



``We could change it up,'' Tattletale said.  ``hit him with enough effects in a way he can't predict.''



``So why don't we?'' I asked.



``Just \emph{look},'' Tattletale said.



Two hundred capes, still recovering.  Some, I suspected, playing dead, morale crushed.



They'd seen Scion's true body.  They'd seen what I'd suspected, that we were truly dwarfed in scale.  Their morale was crushed.



The ones who still fought were the monsters, the lunatics.



King of Cup's power began to recur, massive arms from ten different species, some not from Earth, lunged out of the ground, holding Scion.



Glaistig Uaine.  She had Queen of Swords too, was drawing diagrams between capes on the ground and Eidolon, a narrow, tall image of glowing lines, like a steeple.



The Faerie Queen looked at the Simurgh, and her spirits turned their heads at the same time.  Watching, wanting some kind of action or follow-through.  Expectant.



The Simurgh held one gun.  A single weapon she'd salvaged and sheltered with her body and wings in the instants before Scion had attacked her.



``Silver bullet?'' Tattletale asked.



``It's an air gun,'' Kid Win said.  ``Useless.''



``Maybe there's another use for it,'' Tattletale said.  ``The Simurgh's smart.''



The Simurgh fired the gun.



Scion's hair blew in the resulting gust of wind.



He blasted the Simurgh, sending her into the bay.



While Scion's back was turned, Lung struck.  Brute force coupled with more brute force.  Strength, size, and flames that melted the sand on contact.  Scion was plunged into the molten morass, was subsequently doused in water that steamed in the heat of Lung's flame.



More like plasma than flame, something else entirely.  \emph{Heat}, distilled.  The result was more like Sundancer's power than anything.



Golden light seared Lung's claws, but regeneration and a raw durability that exceeded all reasonable limits gave him the ability to hold on, to keep Scion beneath the growing pool of molten sand.



The light intensified, and Lung's flames swelled at the same time, as if reactive.



The Endbringer-esque Lung fell, as if he had been \emph{pulled} down, and Scion rose from beneath.



Capes who had recovered opened fire.  Glaistig Uaine used Queen of Sword's abilities, created more bindings with the King of Cups.



Crane the Harmonious, as if she'd been waiting for a moment, used her own power.  A sphere, like Sundancer's, only it was a distortion, like a glass bead that made things look upside down when you looked through it.



It moved forward until it was between the defending capes and Scion.



\emph{Once the bead was in place, every} bullet hit.  Every power.



Scion hit the ground, and Lung was on him in an instant, like a cat on a mouse.  It took Scion seconds to fight his way free, to strike Lung aside.



The bead moved, and more shots struck their target.



I watched, very still, as the guns that had been torn to smithereens were reassembled.  The Simurgh was prone, but she used her telekinesis, reaching a distance away.



Scion's beam lanced through Crane.  Too fast to dodge.  It passed within ten feet of me, hit Kid Win, hit the portal.



I could hear a structure collapsing on the far end of the portal.



Crane dropped like a puppet with the strings cut.  Something in Kid Win's suit detonated, and he tipped over, landing hard.



Vista rushed to his side, her expression hard.  No anguish, no tears, none of the emotion I'd have expected her to show.



It was almost scary.



Bastard, in the distance, rose to his feet.



He'd swelled in size.  Was still growing.  Rachel remained where she'd been, kneeling in a pile of his blood, as he tore forwards.



Crashed into Lung, making a sound more like an extended grunt than a growl or a roar.



Lung practically picked up the dog, throwing it at Scion.



It wasn't \emph{additive} growth.  I could see how the dog swelled.  Lab Rat's power had to tap into something to create the flesh.  Had used my blood and bone.  Except it was tapping into the same things that Rachel's power provided.  Mass.



It was like a limiter had been removed altogether.  The can of worms cracked open.  Muscle, rippling.  Claw.  Horn and bone.  Calcified flesh.  Like water from a waterfall, tendrils and body parts raining down from the lump that clung, snarling from many different mouths, to Scion.  All one connected mass, incoherent.



Scion began burning through the flesh, making headway against the growing monstrosity.  Glaistig Uaine shot him with Queen of Sword's ability yet again.



They were driving him away from the settlement, and that allowed some capes to use powers they'd been unable to.  Miss Militia stepped up to the plate, a cape flanking her.



Her power, to create the bomb.  Ten and a half feet long.



Without even being asked, the Simurgh caught it with her telekinesis and flung it.  Scion dodged, and the Simurgh moved the bomb to ensure it hit the target.



The cape beside her used his power to contain the damage, to direct it \emph{outward}, skyward, to shield us from sound, light and shockwave.



The clouds had been struck from the sky.



What remained of Bastard, cut free where the flesh dangled below the erected barrier, fell into the water.   It continued to spread over the Bay's surface and creep towards the beach.



That effect would end before it became a problem, I suspected.



Yet Scion appeared untouched.  He was \emph{cleaner}, even.  Scoured of the blood and dirt.  Pristine.



``A bottomless well,'' I said.



``Bottomless enough to matter,'' Tattletale said.  ``We take out pounds of flesh, but it's really only removing a drop from the bucket at a time.  Then the `water' flows out, high pressure, filling the gaps.''



``And morale plunges,'' I said, staring out at the capes who were hanging back, staring at the scene rather than participating.



``Psychological,'' Tattletale said.  ``Just like Endbringers.  He crafted that body for a reason.''



I nodded.



``We understand him more with every passing moment,'' she said.  ``It doesn't help.  Just the opposite, really.''



I couldn't bring myself to answer.



I heard voices behind us, the noise of thrumming engines.



Reinforcements had arrived.  Chevalier, members of the Protectorate, Leviathan.



And at that same moment, Scion was gone.



I'd grasped, some time ago, that flight added a whole new dimension of possibilities to battle.  Scion brought a \emph{fourth} dimension, capable of stepping out of the fight any time he wanted.



``Running?'' I said.



``No.  Moving on to the next target.  He's going to do a rotation,'' Tattletale said.  ``Hit each area in turn, then go.''



I nodded slowly.  ``Going to do better next time.''



``You didn't do anything this time,'' Tattletale said.



She was right.  I was\ldots what, supposed to coordinate powers?  Pull something?



I'd been on my heels the entire time.  Not scared\ldots



Well, yes, scared.



But more in awe, out of my depth, remembering the last fight and seeing \emph{this} fight, knowing how small I was\ldots  This wasn't a fight that would be won with some gimmicks.  It wasn't a fight that would be won with a \emph{lot} of gimmicks.  I could see it in the trigger-event vision I'd glimpsed, in the way things were playing out, the costs, the lack of any concrete gains\ldots



I shook my head.



``I`m not going to be on the battlefield the next time.''





