





``We knew it would come to this,'' Legend said.



I turned around.  My hands were full as I unbelted a tightly folded blanket and draped it over one of the wounded.



A surprising number of wounded, in the end.  Twenty or so injured from an aircraft that had been partially obliterated, eighteen more people who'd had their legs sliced off.  Nearly forty Dragon's Teeth with mild injuries, their armor melted to their faces, chests, arms and legs.  Scion had tried his usual assortment of attacks, and they'd evaded them.  Enhanced strength from the costumes, predictive technology from the onboard artificial intelligences.



So he'd used a power they couldn't dodge, a power they couldn't block.  A light that radiated outward and melted the materials of their costumes.



Cauldron hadn't been there to reinforce the group.  If they had been, it might have been a staging ground.  Instead, the group had folded and Scion had come after the portal that was closest.



``What do you mean?'' I asked.



``When we were predicting what would happen with the Endbringers, we said that we'd be forced to regroup, consolidate our forces.  Every fight would result in losses, so we'd have to abandon positions, move people from an abandoned post to keep numbers up.''



``I can see that,'' I said.



\emph{An outpost abandoned}.  The world Defiant and Dragon had been looking after was being abandoned as a lost cause.  There were countless people still alive, but they were spread out, and there was no way to mount a proper defense with our forces spread too thin.



``If there's an upside,'' Legend said, his tone changing as if he were forcing himself to be less grim.  ``Tattletale said we're making headway.  It doesn't look like it, but we're taking chunks out of him.  The strongest of us survive, we regroup, see what works, we're stronger when it comes to the next fight.''



\emph{Except he's indiscriminate.  He's killing the ones who can actually affect him, because he's being reactive.  We're not stronger by virtue of the strongest surviving and consolidating}\emph{because the only difference between this fight and the next is that we'll be less.}



I kept my mouth shut.



``Defiant and Dragon will be joining you guys here, to make up for the ones you lost.  You'll have Leviathan, at the very least.  Chevalier and I will be a matter of minutes away.''



\emph{A few minutes is too long}, I thought.  But I didn't want to state the obvious, didn't want to argue.



I was trying to be good, trying not to raise any problems with a guy who could well be sensitive over the fact that I'd murdered one of his closest companions a few years back.



Besides, I knew that this pep talk was most likely Legend trying to reassure the wounded.  Maybe even him trying to reassure himself.



He took his time, putting fresh bandages on a wound.



``I've followed your career,'' Legend said.  ``I've seen you on the battlefields, fighting the Endbringers, old and new.  The bugs are noticeable.''



``I'm nothing special.''



``You rendered Alexandria brain dead,'' Legend told me.  ``That warrants attention.''



``Fair enough,'' I said.  I managed to get another blanket unbelted from the arrangement of straps that kept it in a folded position and then draped it over someone.  Legend moved the end of the blanket, where it rested on the patient's wounded foot.



``I wanted to know who it was that had killed Rebecca.  I kept an eye on everything you did in the Protectorate, looked for the details about your past.  I understand if that seems creepy\ldots''



``I think I get it.  You were close to her.''



``I \emph{felt} close to her.  In the end, though, there was a gap between my feelings and the reality.  Still is, I suppose.  Go through enough with people, build something from the ground up, you form ties.''



``Yeah,'' I said.  I looked over my shoulder.  Mai, one of the kids Charlotte and Forrest were looking after, was there, alongside one of Rachel's henchmen and a puppy.   Giving comfort to a child from the other settlement who'd been burned by the same effect that melted the costumes of the Dragon's Teeth.  The burns weren't \emph{horrible,} but it made it hard to tell the child's ethnicity or gender.



But the child was scratching the puppy behind the ear.  Rachel stood nearby, arms folded, stern and ominous.  I felt a kind of fondness, tempered by a kind of hesitance, like I couldn't let myself hold on too tight to the friendship and familiarity because she could be dead by the end of the day.  Though it was sharper than it had been in the past, it wasn't an unfamiliar feeling.



Legend was looking at me when I turned back to him.  ``Yeah.''



``It doesn't always make for the most sound decisions.''



``No, it doesn't,'' I agreed.  I had to scoot out of the way as some doctors hurried by with fresh tools and equipment.  Removing the dissolved materials from burned flesh was something of a task, and there were a lot of people to help.



``I always knew there was something wrong, underneath it all, but there were bigger things to focus on.  You finish dealing with one Endbringer attack or a potential war with parahuman attacks on both sides, it demands all of your focus.  You're left drained, dealing with the event or the aftermath, and then you need to recuperate, you have an organization to manage.  There's never a moment where you can stop, take a deep breath, and then say, `now is the moment where I address that nagging doubt I had the other day'.  Now is the moment I call so-and-so out on that less-than-complete truth they used while we were elbow-deep in Indonesian cyborg super-soldiers.''



``I think I know exactly what you mean.''



``I think it's very possible you do,'' he said.



``But you can't dwell on it,'' I said.



``If you don't give it the necessary attention, then how do you prevent it from becoming a cycle?''



``You don't.  You look back at your reasons for making the choices when you made the choices, you recognize that you didn't address or act on your suspicions and doubts because you had higher priorities at the time, and you make peace with it.''



``Have you?  Made peace with it?''



``I'm on my way there, Legend.''



``I'm not sure I \emph{want} to go there,'' he said.  ``Give me a hand?  Hold his leg up?''



I nodded.



Gore.  A foot reduced to something unrecognizable.  The man would probably lose it.



But Legend still tended to the limb with care.  Almost gentle.  I tried to be as graceful in keeping the leg in the air.



The soldier made a noise of pain as Legend cleaned the foot, using a laser to sever a tag of flesh that was holding a piece of boot on.  I reached out and held the man's hand.



``You came in here for a reason,'' Legend said.



I looked up.



``It's not about taking care of the wounded,'' he said.  ``You're not devoting a great deal of attention to keeping an eye on Hellhound, either.  Yes, you could use your swarm to discreetly observe her, to discreetly observe anyone in your range, but I don't think that's why you came here.''



I started to respond, but the soldier's leg started kicking, an almost involuntary nerve reaction.  I had to pull my hand from his to hold his leg as still as possible.



We eased it down until he was lying flat, his leg on the bed.  I pulled a blanket over him, as carefully as I could.



``You have a question, or questions,'' Legend said, ``But you're not asking them because you're worried about the response.  Either it's something touchy, or there's another reason why you're holding back.''



I sighed.  ``If you don't have an answer for me, then I'm not sure I know what I'm going to do next.''



``So this is about something only I would know?''



``Basically,'' I said.  ``We don't have access to that broad a pool of people, right now.''



``Okay,'' Legend said.  ``What do you need to know?''



``Cauldron's portals.''



``Closed.  They're created by a parahuman called Doormaker.  The Doctor told me he was blind and deaf to his surroundings, but I think it's far more likely that it's to do with another parahuman she partnered him with.  Someone who grants sensory awareness.  I think the Doctor gave Doormaker too much exposure to this parahuman and destroyed or atrophied his other senses.  One of those nagging doubts I never acted on.''



We passed by Rachel, Rachel's minion and Mai.  I gave Rachel a little nod of acknowledgement as we stepped outside.



Then we stepped outside.  There was a shattered sign over the boarded-up windows.  Apparently Tattletale had made some business deals and tried to get things in place for this to become a city like any one in Earth Bet.  The pieces were there, but the furniture had yet to be installed, the food yet to be supplied.  An empty fast food place, now a makeshift hospital.



\emph{Eat fresh}?  I thought.  Not likely.



I took in the scene.  Capes were still reeling from the attack, and again, it was the monsters and the lunatics that seemed to be standing, while others sat, recovering, catching their breath, mustering their courage.



Nilbog, engaged in conversation with Glaistig Uaine.



Four of the Heartbroken, with Imp and Romp.  A maskless Imp gave Bonesaw a glare as the girl hurried, in the company of Marquis and Panacea, to the fast food place Legend and I had just left.



Lung was alone, looking angry, frustrated, almost more agitated than he'd been before or during the fight.  His eyes were on Leviathan, who was down by the water, but I didn't get the impression Leviathan was the source of the frustration.



Parian and Foil were together, Foil with her mask off.  They'd curled up in a space between two large bins of food, Foil resting her head on Parian's shoulder, their hands and fingers entwined.



Tattletale was caught up in a conversation with Knave of Clubs, and fell under the Simurgh's shadow.  The Simurgh, for her part, seemed to be busy building other tinker devices, drawing on the abilities of tinkers in the immediate area.



Vista was sitting on a rooftop, two stories high.  Her eyes were closed, her hands set behind her so she could lean back a bit.  Her face turned towards the sky.



There were other capes in the area, looking a little more serious, focused on business.  Chevalier was with Defiant and Dragon, Black Kaze, Saint, Masamune and Canary.  Some of them drifted off, making their way towards us.



``If it helps,'' Legend said, ``I don't think Doormaker is dead.  There have been two interruptions in his power, to date.  One followed an earthquake.  He was unhurt, but his partner\ldots well, it was a clue that a partner existed.  His doors all went down simultaneously the moment the earthquake hit the facility.  I don't think his power is the type that would outlast him after death, if it was so easily interrupted while he was alive.''



``So he's alive because the doors are still open in places.''



``Alive and unable or unwilling to use his power,'' Legend said.



I nodded.  ``So is it Cauldron running or is it another agency?''



I could see Legend's expression change.  I'd heard him talk before, saying as much, but his face was what told me, above all else, that he was burdened by regrets.  ``I wish I could say it was the latter.''



``But you don't know.''



``I remain in the dark when it comes to Cauldron.''



``What about Satyrical?'' I asked.  ``He was investigating with his team, wasn't he?''



``He was, but he tends towards radio silence, Pretender's people have since well before the Vegas teams cut ties with the Protectorate.  They claimed it was because there would inevitably be a parahuman who could uncover them if they left channels open.  Now\ldots well, isn't that the way most things were?  Secrets, lies, conspiracies.''



``It is, but-'' I tried to find a way to politely say what I was trying to say.



``But?''



``With all due respect, and I really do mean that because I respect you, I respect that you've participated in the fights, I get where you're coming from\ldots''



``You're spending too much time couching what you're saying,'' Legend said.  ``Rest assured, I can handle what you're about to throw at me.  I think worse things to myself all the time.''



``I'm impatient.  That's all.  Scion's going to attack again, and I don't plan to be here,'' I said.



``You want a portal to get out of here,'' Legend said.



``No,'' I said.  ``I don't want an escape.  I want to \emph{act}.''



``We're acting,'' Legend said.



``We're \emph{reacting}.''



``If you have ideas for something pre-emptive, I think we could all stand to hear it.''



I shook my head.  ``Nothing definitive.''



``Even something that isn't definitive.''



``I want to find Cauldron.  They have contingency plans we know they haven't put into effect yet, and they have answers they've yet to provide.''



``Cauldron is very good at leading people to believe that they have the answers and then disappointing,'' Legend said.  ``Take it from someone who knows.  Ah.  I'm doing it again, aren't I?  Like an old man.''



He smiled, and I smiled a little too.



``You're an old man?''  Chevalier asked.  His group had just joined us.



``Taylor here was just very politely trying to tell me I'm wasting her time on reminiscing and regrets.''



``You have something better to do?'' Defiant asked me.



``\emph{Defiant},'' Dragon said, admonishing him.  She was in her armor, but had her helmet off.  The face was real.  Plain, but real.



\emph{She's an A.I.  A false person.  What else had Saint said?  She's deceiving us?  It's all an act}?



``\ldotscame out wrong,'' Defiant was saying.  Very deliberately, he said, ``I am genuinely curious what you're doing, Weaver.''



Dragon smiled a little, as if a private thought had crossed her mind.



The doubts Saint had seeded dissipated.



Ninety percent of them.



``I was telling Legend I want to go after Cauldron,'' I said.  ``A member of the Chicago Wards was saying that sending Satyrical to go investigate is like sending a fox to guard the henhouse.''



``Satyrical has definite ties to Cauldron,'' Dragon said.  ``If nothing else, Pretender maintains connections to the group.  If Cauldron \emph{is} running, or if they are pulling something covert, then it's very possible Satyrical is on board or is going to be brought on board.''



Chevalier shifted the Cannonblade to his other hand, then stabbed the point into the ground.  It looked different.  His \emph{armor} looked different.  Gold and black, instead of gold and silver.  ``It also means he and the Las Vegas capes are well equipped to know how Cauldron operates, and identify clues others would miss.  We sent them with others we could trust.  They've been reporting in on schedule.''



I opened my mouth.  Chevalier spoke before I could.  ``-\emph{With }stranger and master precautions in place.''



I frowned.



``You're strong when it comes to improvising,'' Chevalier told me.  ``We've got a moment to breathe.  We think he's hitting another world, one we don't have access to.  We're regrouping, figuring out who goes where, and we're trying to set things up so we can mobilize faster.  I can't tell you what to do.  I wouldn't if I could.  But we could use you here.''



``We're \emph{losing}, here,'' I said.  ``Legend was being positive, but\ldots I don't think we can really delude ourselves that far.  He's tearing us apart while holding back.  If we put up a fight or if we don't hold back, he hits us harder, like he hit the Guild.  He can always top us, and he can always say he's had enough and then just nuke the continent.  That's not a recipe for an eventual win.''



``I don't even think that's the worst of it,'' Tattletale said, finally having broken away from Knave of Clubs to join this conversation.  ``He's evolving, maturing.  If you can even call it that.  He was a blank slate, then almost like a baby, flinging destruction around like a baby practices moving their arms, as if to remind himself he \emph{could}\ldots and then he was like a child in this fight\ldots except for the bit about Queen of Swords.  That suggested he's almost entering an adolescent phase.  Something more complex than just raw fear and awe.  Loss, despair.  He's going to start looking for ways to \emph{really} hurt us.''



``Instead of just annihilating us?'' Legend asked.  ``Torture?''



``Mental, emotional, more involved physical torture.  Up until he hits adulthood.  Then he probably destroys us, completely and utterly.  I'd be surprised if we lasted more than two days, rate he's developing.''



``You're talking about him as if he were human,'' Saint said.



``He \emph{is},'' Tattletale said.  ``It's the only reason he's doing this, and it's the only way we have to truly make sense of him, and it's his primary means of making sense of \emph{us}.  Which is why he did it.  He's got our general biological makeup.  He thinks, he feels, he dreams, he hurts, but it's all buried so far under mounds and mounds and mounds of power and security, it doesn't really supplant \emph{him}.  It's never been exposed to the real world, really, so the human side of him hasn't matured or developed.''



``A weakness?''  Chevalier asked.



``Yes, but not a weakness we're going to be able to exploit,'' Tattletale said.  ``He's too careful, and he would have foreseen it.  Adapted around it, probably.  Be \emph{awfully} stupid for something like him to adapt traits of their targets and adapt vulnerabilities at the same time.  Knowing this could help, but it's not going to be the weak point we can target to finish him off.  That makes \emph{zero} sense.''



``We know a lot of things like that,'' I said.  ``A lot of tidbits about his behavior or who he is or what he is.  But a lot of it isn't reliable information.  He cared a lot about my clone decoys multiplying during the fight on the oil rig, but he didn't give a damn this time.''



``He's advancing, evolving.  His focus is changing,'' Tattletale interjected.



``We know so many critical details,'' I said, ``And we need more.  We need a way of paring truth away from fiction, or determining what's \emph{no longer} true.  I don't know for sure what we're going to do to stop him, but I think any plans I have are going to start or end with Cauldron.''



I looked around the group.  Men and women, all in armor that made them stronger, bulkier or taller, it seemed.  Legend was comparatively small, but he had presence to make up for it, even as tired and worn out as he seemed to be.  Flying, casual flying as Legend tended to do, gave one a little more stature.



I wasn't short, but it felt like Tattletale and I were mortals in the midst of giants.  Defiant, in particular, seemed somehow imposing.  His body language was familiar with the way he'd naturally set his feet apart, his hand on his weapon.



Even the place we were standing, it stirred memories.  We were at the north end of the Bay, even.



``Yes.  The plan makes sense,'' Defiant said.  ``I'll trust you on this one.''



Dragon reached out to grab and squeeze his hand.



``What do you need?'' Defiant asked me.



``I was thinking I'd bring some of the capes that can't or won't participate in the fight against Scion,'' I said.  My eyes fell on Canary.



``\emph{Me}?''  Canary squeaked.



``Anyone, but capes \emph{like} you,'' I said.  ``Support capes who can't support in circumstances like this.  Strangers who can't use their power on Scion.  Capes like that.''



``And if you can't access Cauldron?'' Chevalier asked.  ``I don't want to put too fine a point on it, but your actions when you assumed control of the Simurgh were\ldots heavy handed.  You told an ex-teammate in the Wards that you weren't intending to be a hero anymore.  I don't want to tell you I won't cooperate any more than I want to tell \emph{anyone }I won't cooperate, but you'd be asking us to put a fair amount of power in your hands by sending capes your way.  I\ldots don't know that I feel confident sending capes to you, if I don't know how they'll be put to use.''



``Would you allow me to \emph{talk} to other capes?'' I asked.  ``You don't have to send them my way, but maybe I could inquire?''



``I'm not going to stand in anyone's way,'' Chevalier said.  ``I'm not the bad guy, here.  But I've got to lead this battle, and I've got to do what I can to make sure things don't get worse.  If a cape needs to go, if they don't have the courage to stand and fight, I'm not going to make them.  I'll try to convince them otherwise, but I won't make them.  And if they think they'll be more useful elsewhere, I won't stop them there, either.''



I nodded.  ``I'll settle for that.''



``What else?''



``Access to computers,'' I said.  ``Tools.  Resupplies.  The Dragonfly.''



He reached out of his pocket and withdrew a knife.  He reversed it and extended it to me, handle first.



I reached for the weapon, then saw Defiant pull his hand back.  ``Be aware of the safety and the activation switch.''



I saw one of the switches, then took hold of the knife.



``Keep it away from heat.  If the growths start knuckling together, then it's probably clogged at the air intake.  You can unscrew the cap at the butt of the knife and access the air intake there.  Bake it at roughly five hundred degrees to clear it, then thoroughly vacuum.  Pay attention to how long it takes the growths to hit maximum length\ldots you'll know because the colors at the ends are a lighter gray.  Three point seven seconds is the optimum time.  If it takes shorter then you'll know something's wrong with-``



``The knife won't degrade too much in the next day,'' Dragon said.  ``And we \emph{have} spares, thanks to Masamune.''



``You didn't make this much of a fuss with my flight pack,'' I said.



``I included documentation,'' Defiant said.



``Thank you,'' I said.  I found the holster for my old knife, then put it through the belt at my back, holstering the new knife.



``Where's the Dragonfly?'' he asked.  I pointed.



Dragon said something in Japanese to Masamune and Black Kaze.  There were two nods.



Defiant led the way to the Dragonfly, all business, Dragon, Canary, Tattletale, and me following.  He seemed almost happy to have something to focus on.  A problem that could be solved.



Did he \emph{genuinely} trust me?  Was there a modicum of hope, here, with me mobilizing to go look into the Cauldron situation?



He continued to hold his weapon, though the fight wasn't about to start.



I could imagine his outlook, the security the weapon afforded him, a hundred solutions in his hands.  The ability to defend himself, to defend others, to move out of the way of danger.  It made sense.



Dragon, conversely\ldots what was her security blanket?



Different.  I couldn't put my thumb on it.  But she'd lost to Saint, to the Dragonslayers.  She'd been taken captive, effectively killed.  Killed by a man who saw her as subhuman.



She'd been altered by Teacher.  Not so much she was a slave to him, but \emph{something} had happened, and that was no doubt a large part of how she was disconnected from reality in the here and now.



I looked back at Saint, Masamune and Black Kaze.  Saint was taking a seat, his back to a chunk of destroyed aircraft, cross-legged.  Calm, relaxed.



``How can you stand to be near them?'' I asked.



``Keep your enemies closer,'' Dragon said, her voice tight.



``Don't forget about the friends part,'' I said.



She shook her head a little.  ``I won't.''



``When we were waiting for the fight to start, I went around, looking for people I needed to thank.  Important people to me, people who I wasn't sure I'd get a chance to talk to again.  I missed a few important ones.  My dad\ldots you two.  I know the only reason I got my shot at being a hero, the only reason I didn't go to jail, was because you vouched for me, because you agreed to cart me back and forth and interrupt your schedule.  I probably didn't even deserve it, but you backed me up.  I'm just\ldots I've never been good at saying thank you and sounding as sincere as I feel.''



``I think we benefited as much as you did,'' Dragon said.  ``You needed to join the Wards to\ldots make amends, shall we say?  It was the same for us.''



``For me,'' Defiant cut in.



``I had my own regrets,'' Dragon said.



``You had no choice.''



``Regrets nonetheless,'' she said, again.  Her head turned towards Canary, and Canary smiled just a little.  Dragon then looked to me.



Was it possible for an artificial human to look weary?  To look \emph{wounded}, in the sense that she was bearing some grievous injury from recent events?



We'd stopped outside the Dragonfly.  I bid the ramp to open, controlling the bugs in the operating mechanism.



Then, as it opened, I impulsively gave Dragon a hug.  Returning a favor she'd given me some time ago.



``Let's get you set up,'' Defiant said.



``Hook me in while you're at it?'' Tattletale made it a question.  ``Whatever you need to do, so I can communicate with her and her peeps.''



``I'll see to it.''



Tattletale glanced at me.  ``Ops?''



``Please.''



\sectionbreak



We circled twice before coming in for a landing.  A cave just above water level, inaccessible except from the air.



The receiving party consisted of Exalt and Revel from the Protectorate core group, with half of the Vegas team.  Nix, Leonid, Floret and Spur.  Vantage was waving a rod around, listening to steady beeps.



``Oh god, \emph{finally}.  \emph{Something} to take my mind off the beeping,'' Floret said.  She was petite, her hair in carefully layered waves of pink, with green at the roots.



``Find anything?'' I asked.



``No signs of any portals that have been opened in the past.  Harder than cracking Dodger's gateways, apparently,'' Vantage said.  ``Or they gave us bad instructions.  How're you doing, Weaver?''



``I'm fine,'' I said.



``Wearing black,'' he said.



``Is \emph{everyone} going to comment on that?'' I asked.



``It's comment worthy.  How'd the fight\ldots nevermind.  I can guess.''



``Probably,'' I said.



``Grim group,'' Floret commented.  ``I know black's `in' with the end of the world, but damn.  Only one person with style.''



I looked over my shoulder.  Golem, in silver and gunmetal, his mask solemn.  Cuff, again, in a dark metal costume.  Imp, with her dark gray mask and black bodysuit that actually fit her.  Shadow Stalker, in a black, form-fitting bodysuit like the one I'd given Imp, along with a flowing cloak with a heavy hood.  All spidersilk, but the mask was hers, as was the crossbow.  Rachel followed, her jacket, tank top and pants black, only the fur ruff at her shoulders, where it flowed around the edges of her hood, was white.  Huntress and Bastard flanked her.  Lung was still inside the Dragonfly, but I knew he had only his mask and jeans on.  Barefoot, shirtless.



Canary was the only one, apparently, who met Floret's standards.  Yellow body armor, her helmet in one hand, her hair and feathers free.



``I remember you,'' Spur said.  He smiled.  Teeth that had been professionally done, no doubt.  He wasn't bad looking, but not quite my type.  Spiky hair, and a costume that mingled barbed wire tattoos with real barbed wire, where his skin was exposed.  Mid twenties, with hair bleached to a near-white and acid washed jeans.  His mask was simple, black, covering the upper half of his face, with only a circle of barbed wire at the brow.  A trademark of thinker powers, to do the whole forehead thing.  A precog who was most effective in the midst of chaos and heightened emotions, and fairly competent otherwise.  ``Bad Canary?''



Canary's eyes widened.  ``You remember my stage name?''



``You were famous,'' he said.  ``The whole trial thing.  You-``



Canary's expression fell.



``-got robbed,'' he said.



``\emph{Dick,}'' Floret said.  ``Like that's how she wants to be remembered.''



``I remember the music too,'' he protested.



``Yeah,'' Canary said.  She rubbed the back of her neck, avoiding eye contact.  ``It doesn't matter anyways, does it?  Long time ago, and we've got better things to worry about.''



``\emph{Vulgarishous},'' he said.  ``\emph{Ur-sound}?  \emph{Lineless}?''



``You're probably cheating,'' she said.



``I could sing the lyrics,'' he answered.



``It would make me \emph{sure} you're cheating.  \emph{I} barely remember the lyrics.''



``I don't believe that for a second,'' Spur answered her.  ``Eh, guys?  Back me up.  My power doesn't give me a way to cheat, does it?''



``No,'' Floret said.  ``He's genuine.  And none of \emph{us} have ways to clue him in.''



I glanced at Revel, who only rolled her eyes a little.  Exalt looked bored.  He saw me looking and commented, ``It's fine here.  We're using substandard tools to find a portal that used to exist, and we don't know exactly where it was.''



Imp pushed her mask up until it sat on top of her head.  ``Finding a transparent needle \emph{outside} of the haystack.''



``Well put,'' Leonine said.



``Don't encourage her,'' I told him.



He only smiled, which made Imp smirk at me in turn.



Spur was murmuring the lyrics to the song, and he was actually doing a good job of it.  Canary was \emph{trying} to look like she wasn't pleased as punch.  It was cute.  Cute and just a little ominous, considering who these guys were.



Some things had come to light after they'd departed their positions in the Protectorate and Wards.  Nothing definitive, but it raised questions that had yet to be answered.  Questions that would probably never be answered, now that evidence lockers and court records throughout Earth Bet had been obliterated.  Problems that had resolved themselves just a little too neatly.  People, both bad guys and witnesses, who'd disappeared.



``If I'm the lion, and you're the goat\ldots'' Leonine was saying.



``I \emph{guarantee} I'm more dangerous than you,'' Imp retorted.



I could sense others in the group getting restless.



``We'll let you know if anything turns up,'' Revel said, as if she'd sensed it.  She smiled a little, a bit awkward, or apologetic.  ``Don't let us waste your time.  It's the end of the world, spend it with people you care about.''



Her eyes moved to Cuff and Golem, who were hanging back.  The pair were the heroes of our group, so to speak.  They'd feel the betrayal of the Vegas capes more sharply, even now.  They looked at each other.



I did too.  Not that I counted myself as a hero.  But I'd \emph{been} there.



``I could come with,'' Exalt said.  ``If you're going back.  I'm only here to relieve Revel.  I'll be able to participate in the coming fight.''



``Sure,'' I said.  ``But I'd like to hear the password.  From Revel.''



``Good thinking.  Belord, six-two, spauld,'' she said.



``On my seventeenth birthday,'' I said.  ``What color was the cake?''



``Seriously?'' she asked.  ``Do \emph{you} even remember?  I should get a brownie point for this one.  Because I care about my Wards.  It was white.''



``The frosting?'' I asked.



``Blue,'' she said, sounding just a bit put out.  ``And you barely ate any.''



I nodded, satisfied.  ``And\ldots Leonine.''



``\emph{Me?}''  Leonine laughed a bit.  ``What kind of shenanigans do you think we're pulling?''



``He's one of the Vegas capes,'' Imp said, speaking very slowly, like I was mentally disabled.



``I \emph{know} he's one of the Vegas capes.  But I think I have to cover all of the bases.  Who was your kindergarten teacher?''



``You \emph{researched} that?'' Spur asked.  ``Dug through our entire histories to find something obscure?''



He sounded offended.  Every head had turned his way.



``Do you have a problem with that?''  I asked.



He frowned, but he shook his head, sticking his hands in his pockets as he leaned against the wall beside Canary.  ``No.  No problem.''



``Richie,'' Leonine said.  ``Mrs. Richie.''



``Great,'' I said.  ``Great.  Now let's drop the fucking act.''



``I gave you the answer you wanted,'' Leonine said, smirking.  ``What the fuck?''



``Spur?'' I said, ``Raise your right hand?''



He did.  There were bugs on the fingers.



``He was moving his hand.  A one-handed sign language.  I assume everyone on your team knows it.''



``I was thinking of Canary's music,'' Spur told me.  He stepped forward, putting a hand on Canary's shoulder as he did so.  She turned, so they were both facing me.  ``Piano keys.  Mnemonic tool.  \emph{That} is something our team uses.''



``You're being a \emph{little} crazy paranoid,'' Imp said.  ``Just a little.''



``They've been playing us since the start,'' I said.  ``The men were batting their eyelashes at you and Canary, probably the targets they thought they could work.  Revel\ldots I'd think she's under some kind of compulsion.''



``A \emph{lot} crazy,'' Imp said.  ``Way crazy.''



``Maybe Tattletale can chime in,'' I suggested.  ``Tattle?''



``\emph{Mostly right.  Exalt, Revel, Vantage, Leonine, Floret, all fakes}.''



``No shit,'' Imp said.  Her mouth dropped open.  ``No \emph{way}.''



``Jig's up,'' I said.  ``We know.''



One by one, the Vegas capes changed.  Flesh altered, and they assumed identical appearances.



Six copies of Satyrical.  Leaving only Spur and Nix.



One of the Satyricals looked at the two who remained.  ``Take care of yourself.  I'll see you shortly.''



``I know,'' Spur said.



Satyr looked at us, as if taking us all in.  ``And \emph{you}, I suppose, we'll run into.  Sooner or later.''



Then the Satyrs died.  Flesh withered, and the Satyrs crumpled up.  They made bloody messes as they hit the ground, like overripe tomatoes might, but with teeth and the occasional bit of withered organ.



Self duplication, and each duplicate had shapeshifting abilities.



I bent down and picked up the devices from the heads of Revel, Exalt and Vantage's clones.  Earbuds, phones\ldots



``Revel,'' Cuff said, her voice small.



``Where are the real ones?'' Golem asked.



``With the real Satyr,'' I guessed.



``And how did he know the passwords?'' Golem asked.



``\emph{He guessed the cake thing through cold reading.  White with blue, like Weaver's costume.  Made sense.  That Taylor didn't eat much\ldots well, look at her}.  \emph{The rest\ldots torture?  Coercion through other means?''}



``Torture?'' I asked.



Spur raised his chin a bit, but didn't do or say anything to suggest otherwise.



``Ew.''  Imp said, under her breath, ``Ew, ew, ew.  He's like, \emph{forty}?  And he was \emph{hitting} on me.''



``Where's the portal?'' I asked Spur, ignoring Imp.



``No portal.  Or weren't you paying attention?''



I looked at Nix.  ``You know where this goes, if you don't cooperate.  Circumstances are a little too dire.  We knock you out, your power fades.  So why don't you drop the illusion and let us see the portal?''



``My power stays up while I'm out,'' she said.



I drew my knife.  The one that wasn't special.



``Woah,'' Golem said.  He put his hand on my wrist.  ``Woah, woah, woah.''



``She's bluffing,'' Spur said, unfazed.  ``She's scary, she's got a reputation, but she's bluffing here.  There's no way she follows through.''



``I think you're \emph{badly }underestimating how pissed off I am,'' I said.  I was surprised at just how right I was.  The mounting anger caught me off guard.  ``Doing this, screwing around, stabbing people in the back, screwing with the system when we're trying to save \emph{humanity}?''



``We're saving it too,'' Spur said.  ``Satyr, the others, they've got this situation handled.  Give them\ldots two or three more hours, and the threats are going to be dealt with, Cauldron will be secure, or as secure as they can be, after you account for injuries and deaths at the hands of the invading group.  You go in there, you're just going to muck up a delicate exfiltration operation.''



``Invading?'' Golem asked.



``The deviants.  The case-fifty-threes.  Weld's group.''



\emph{Weld}?  No.  He'd been one of the only decent ones out there, during my stay in Brockton Bay.  Respectable, honest, kind.  He'd saluted me the first time we'd crossed paths, because we were both going up against an Endbringer.



Fuck it all.



Either Spur was fucking with me, or things were fucked.  Fuck it all.



``People like you are the reason we deserve to lose,'' I said, gripping the knife.  ``Every step of the way, it's been people refusing to cooperate, refusing to talk plain truth.  From day one, even.  \emph{You're} the reason humanity deserves to get wiped out.''



``Great,'' he said.  ``You're still not going to use that knife on either of us.''



It was said with the smug tone of someone who could see the future.



I glanced at Canary.  I could see the hurt on her face.



``I get it,'' Spur said.  ``See it coming.  If it helps, I \emph{do} remember the music.''



Rachel stepped forward, giving me a little push to get me out of the way, and then slugged him.



He dropped, unconscious.



Golem set about binding him to the cave floor with hands of stone.



I looked at Nix.  ``Her too.''



Golem reached into his costume, and hands of stone gripped Nix.



``To the ceiling,'' I decided, at the last second.



``Sure,'' Golem said.  Hands of stone emerged, passing Nix up.  She struggled a bit, but she was at an unsafe height by the time she realized what he was doing.



She was bound to the cave ceiling with armholds, leg holds and an arm set across her collarbone.



``What the hell?'' she asked.



``I don't think any of your friends have powers that can break those hands,'' I said.



``The hell?'' she asked, again.  She tested her bonds.  ``The \emph{fuck}?''



``You better hope we make it out okay,'' I said.  ``Tattletale?''



``Pretty sure it's to your left.  Start by going ten paces that way.''



I nodded.



We followed the directions.



The illusion broke, dissolving into harmless smoke, as we reached it and pressed hard enough against the wall in question.



With the barrier gone, I could feel the warm air from within, see a dark hallway without lights.



I looked at my teammates.



\emph{Maybe humanity deserves to lose, but these guys are why we're going to win, }I promised myself.





