





Lights flickered as we made our way inside.



It looked like a hospital, but not an abandoned one.  Things were pristine, the walls and tiled floor a clean, untouched white.  It wasn't a place that had been left to deteriorate.  The stark, clean nature of the place made for a contrast where the damage had been done.  There were gouges in the walls, things torn free from walls and ceilings.  Scorch marks, from both acid and fire, and damaged chairs, cabinets and lockers.



I noted the contents of the lockers and cabinets that had been torn open.  Glass vials, empty, clear fluids, medical tools still in plastic wrappers with paper covers that could be torn away.  But for the disorganization, it was all in excellent condition.  It didn't look like it had even been touched.



The longer I looked, the less it seemed like a hospital, and the less \emph{real} it seemed.  It was more like someone had taken sections of a hospital, removing everything like the nurse's stations and the rooms for the patients, leaving only the hallways and doors that sat flush against the floor, airtight.  I would have thought it was all staged, but a check with my bugs confirmed that there was a minimum of dust even in places people wouldn't be able to see.



Why take that much time to clean areas that were never going to get used?



``Tattletale?'' I asked. ``How's the connection?''



``\emph{The Dragonfly is relaying the connection from the towers, which are relaying from Gimel.  Kind of impressive when you think about it.}''



``I'm thinking this stuff tells a story.  Can you fill us in?  Information wins fights.''



I heard a noise from behind me.  A grunt or a scoff.  I turned to look, but couldn't see who it had been.  Lung?  Shadow Stalker?  Golem?  Cuff?  All were possible, on different levels.  Lung might have been dismissive, Cuff bemoaning the fact that I was harping on that particular point yet again.  I'd reiterated it a few dozen times when justifying the stakeouts and a few cases of infiltration.



``I can see the path they took\emph{,}'' Tattletale said.  ``\emph{You're facing the direction the Irregulars headed.  They got more agitated as they made their way through.  Excitement, anger, a mess of negative emotions, bottled up for years, finally released.}''



I nodded.  I could imagine it now, almost see them in the hallway.



\emph{``Forty three of them.  Case fifty-threes.  Weld's entire group.}''



``We have data on them?'' I asked.  My eye fell on one of the doors.  It looked so ordinary, but someone had hit it, and it had been \emph{dented}.  Metal, and apparently well reinforced, with a good section of the door fitting into the wall.



``\emph{Already have files open.  There's not a lot of details on most of them, but they aren't exactly in the public eye.  You only get sightings, and apparently PRT paperwork where Protectorate members get sent to check in on them every once in a while, make sure they're okay.  The others, well, you're aware of Weld and Gully and Gentle Giant.  I could recap for the people who wouldn't know.''}



``I know enough,'' Lung said.  ``I would rather not have a voice prattling in my ear when I could be listening for trouble.''



``Oh, hey,'' Imp said.  Through the bugs I'd planted on him, I could feel Lung reacting to her sudden appearance.  ``I wouldn't mind hearing this info.  Cliff notes?''



``You're doing this to irritate me,'' Lung said.



\emph{He's sharp, in some ways,} I thought.



``Don't get your \emph{gonads} in a twist.  I just want to know what we're walking into.''



I heard a growl, and my first thought that Imp had pushed the wrong button.  I turned, my hand moving to my knife.



But it was Rachel's dog, Huntress, her nose pressed to a door.



I watched each of the others prepare for a fight.  Or \emph{not} prepare, as the case was.  Lung remained very casual, almost calm, while Canary backed away, putting as much distance between herself and the door as she could.  She was in better armor than most of us,with one of Saint's Dragonslayer suits, but she still saw herself as vulnerable.



Hell, \emph{I} saw her as vulnerable.



My bugs moved around the door's perimeter, but I could sense only damage around the handle.  As airtight as any door.



I drew my knife, then gave Rachel a nod to go.



She kicked the door handle, and the door swung open.



Blood, corpses.  Three dead case fifty-threes.  Two men and a woman.  A cat-man with far too many teeth in his mouth, even covering the roof and the space beneath his long, narrow tongue, something that looked like keyboards on his forearms.  A reptile, not so different from Newter, but with no mouth or nose.  Only two overlarge eyes.  The last was a girl, squares of flesh intersped with patches of cloth.  Her mouth was only a tear in the cloth.



Their throats had been neatly slashed -the patchwork girl bled like anyone else might- and they'd been dragged into this room.  It was clear from the way that the blood trail suddenly \emph{stopped} that someone had cleaned up.



``\emph{Stragglers.  The Irregulars were moving as a tight group, keeping close to one another, but Satyrical and his team blindsided the ones at the back.  Killed them, dragged them off, then one of them cleaned up the evidence.  Floret, probably.''}



``And Satyr probably masqueraded as these three,'' I said.  ``He's in Weld's group.''



``\emph{Probably}.''



``Then we need to move fast,'' I said.  ``Good job Rachel, Huntress.''



Rachel only grunted acknowledgement.



``You're \emph{thanking} the dog?'' Shadow Stalker asked, incredulous.



``I'm thanking people that are being useful,'' I said, my voice hard.  ``If you want to be one of them, maybe scout the rooms we're passing by.''



She didn't obey right away, but she did obey.  She disappeared through a door.



The lights momentarily went out.  For an instant, I thought Shadow Stalker had been electrocuted, walking straight into a wire.  They flickered on again.



There were no windows, no sources of light beyond the lighting that was supposed to glow evenly from the high ceiling above.  When the lights flickered out again, the darkness was absolute, all-consuming.  As seconds creeped on and the light failed to return, I wondered if we'd be continuing this in the dark.



Lung used his power, creating a flame in his hand.  It didn't make for much light – only enough to illuminate our groups.  Golem raised his hand to his helmet, then paused.



``Go ahead,'' I told him.



The lights mounted on Golem helmet turned on, followed soon after by Cuff's own lights.  I could see the way they were turning their heads, trying to cover both ends of the hallway.



``I don't sense anyone,'' I said.



No.  Wait.  There \emph{was} someone.



Something.



I'd sensed it at the meeting the Doctor had arranged.  The spirit, the ghost.  So subtle it was almost impossible to notice.  The currents of the air, the faintest of traces in dust that marked where she'd traveled\ldots all things I'd mentally dismissed.  Air tended to move.  Only the fact that this was a closed space, without any kind of air conditioning or temperature difference made the movements in the air curious.



Paying attention,  I could see that there was a pattern, a consistent repetition in air currents so feeble they might not have moved a feather.



The lights flickered back on, went out, and then settled in a compromise, the dull translucent pane of the ceiling lit up with a patchwork of  maybe two thirds dark to one third light.



``We're here to help,'' I called out.



My voice echoed down the hall.



``I thought you didn't sense anyone,'' Canary said.



``I don't,'' I said.



``Then who are you talking to?''



``I don't think it's a who,'' Imp said.  ``Try `what are you talking to?'''



``Shh,'' I bid them to be quiet.



I could sense more movements in the air, close\ldots no.  That was a result of Lung's fire heating the air.



Further down the hall.  \emph{If I use enough bugs, try to get a sense of dimensions\ldots}



A head, part of a torso.  I could feel the contours of narrow shoulders, the waist.  Female.



She disappeared, or she became less coherent, the movements in the air continuing, but ceasing to suggest a general human shape.  Another appeared behind us, roughly as far away.  No arms, no legs.  Just a broken figure.



``Help me out, Tattletale?'' I asked.



``\emph{Help with what?}''



``The Custodian.''



``\emph{I'm not getting anything usable,}'' she said.  ``\emph{Video cameras suck like that.}''



``Right,'' I said.  Louder, I called out, ``We're here to help the Doctor!  You've got two other groups in here, one that's definitely hostile, angry and destructive, and another I think is worth being suspicious of.''



A movement, a reaction to that last sentence.



I explained, ``Maybe they \emph{seem} friendly, but they've got a bad history of backstabbing, making subtle plays for power.  I think the Doctor would back me up on this.  If she's cooperating with them at all, she's doing it with knowledge they'll capitalize on any weakness she shows\ldots and she's never been weaker than she is right now.''



The figure turned around, briefly fading out of existence.



She reappeared in a way that made me wonder just how long she'd been there, a foot away from me.



``We're \emph{not} your enemies,'' I said, holding my ground.  ``I want to stop Scion, and the best, easiest way to do that is to get things back into working order here.''



For an instant, she was in four places at once.  Then she settled on three.



It struck me that I'd never fared particularly well against stranger-class powers.



``If it helps,'' I said, ``I'm \emph{pissed}.  The Doctor called you the Custodian, which probably means you're the one taking care of this place.  If you're not completely emotionless, it \emph{hurts}, that they're tearing it apart.  If you care about the doctor, I'm betting you're worried.  Maybe you feel like I do.  You want to retaliate, but \emph{something} is getting in your way--''



And then she was gone.



``So.  Uh.  You're kinda tense there, boss,'' Imp said.



``She's gone,'' I said.  ``I'm pretty sure.''



``Question is, is there \emph{reall}\emph{y }a crazy janitor lady?''  Imp asked.  ``\emph{Or} is Skitter finally going mad?''



``If there are no more obstacles, we should go,'' Lung said.



I nodded.  I started walking at a good clip, reorganizing my swarm to check the areas around corners.



A series of eight or so doors to our right were open, now.  Shadow Stalker lurked at the end of the hallway.  She must have walked through the walls while the power was out, opening every door in passing.



``Just saying,'' Imp kept talking, ``Custodian?  Knowing what we do about your origins\ldots kinda a thing.  The Doctor, if you think about it\ldots what if we're \emph{all}--''



``Imp,'' I interrupted her, all too aware of the presence of Lung and Shadow Stalker, ``Not now, not here.''



``Righty-o.''



\emph{She's nervous}, I told myself, before I could get too irritated.  But her way of dealing with that came at my expense.  I didn't need to be reminded of my weakest moments.



I \emph{really} didn't need any head games, intentional or otherwise.



With the doors open, it was possible to see the room interiors.  Offices, perfectly ordered and empty of people.  Desks, file holders to neatly sort paperwork, book cases with texts.  All of it even, ordered.  No pages sticking up or books missing from shelves.



``\emph{Still want that briefing, Imp?}'' Tattletale asked.



``Huh?  Briefing?''



``\emph{On the Irregulars.}''



``Oh.  Right.''



``\emph{I'll take that as a no}.''



I sent my bugs out, directing them to collect a few things.  Two booklets, the most substantial material my bugs could hold and still carry.



``\emph{They shouldn't have been able to pull this off,}'' Tattletale said.



I thought of Contessa, and of the Custodian.



``They did, though,'' I said.  ``At the worst possible point in time.''



``Weld isn't dumb,'' Shadow Stalker said, as she stepped out of one room and crossed the hall.  ``Except maybe with people.  Kind of put his big metal foot in his big metal mouth, I remember.  But he's not dumb when it comes to powers or strategy.  He's had a few years to figure this out.''



``Hey,'' Imp said.  ``You're not allowed to say nice things about people.  You shot my brother with an arrow, messed with people I respect.  I've been waiting for that cinematic moment when you and I find ourselves alone and I get my revenge.  Don't fucking dilute it by being \emph{nice}.''



Shadow Stalker stared at Imp, standing her ground as we, Imp included, made our way up the hallway to where she was.



``You're \emph{irritating},'' Shadow Stalker said, her voice dripping with condescension, dismissive.  That said, she disappeared through the nearest door.



``\emph{Better},'' Imp muttered.



I used the arms on my flight pack grab the booklets my bugs had brought to me.  The contents of each were bound into books.



I paged through the booklets.  The cover of the first read: `ASDEC01 Employee responsibilities, contingency C-2-6'.  The second was `ASDEC01 Employee responsibilities, contingency F-4-7'.  Both, at a glance, very similar inside.



I looked at the inside cover.  \emph{Contingency C-2-6.  Transmigration.}



Then page upon page of jargon.  References to other files, to organizations and places I had no concept of, and things I knew of, but not in this context.  Overseers, terminus, and again, the word transmigration.



It lacked flow, as the writing went.  More of a technical manual, in the end.  I could tell from the structure that things had been done by computer, so that information specific to the employee and the employee's role could be injected at the appropriate spots.



I flipped through the book, continuing to scout with my bugs and use them to check our surroundings for possible danger.  Only endless hallways.



``You reading over my shoulder, Tattletale?'' I asked.  I had the camera on my mask.



``\emph{I am}.''



``Thinking what I'm thinking?''



``\emph{Accord was two-timing us},'' Tattletale said.  ``Doubling up so he had enough of a power base to enact his plans, whatever happened.''



``Except for, you know, the whole dying thing,'' Imp added.



``Are you getting the gist of this, Tattletale?''  I asked.



``\emph{Picking up pieces of it.  I'd ask you to scan the thing and let me have access to all of it, but that's not exactly reasonable, is it?}''



``Just give me the byline.''



``\emph{A plan for if the Endbringers win.  A plan for if Scion wins.  A plan if we come out ahead and beat both of them.  Recurring themes in all of the plans.}''



``No plan survives contact with the enemy,'' Lung rumbled.  ``Foolish.''



``\emph{Accord makes pretty fucking good plans,}'' Tattletale said.



``I do not know this Accord, and I only trust what I experience myself, so this is only prattle to me.''



``How does this turn out?'' I asked.  ``Cauldron ruling the world?''



``\emph{Honestly?  I don't think so.}Cauldron's primary interest seems to be humanity.  Keeping us going, minimizing chances of war and conflict.  All of this seems to be geared around that.  Setting things up so we aren't fucked, however things go down.''



``Right,'' I said.  ``Where do the powers come in?''



``\emph{I think\ldots well, I don't have enough to say anything for sure.  But the underlying assumption seems to be that parahumans are going to take charge, one way or the other, so they wanted to set things up so that happened naturally.  They've been vetting clients, finding the ones who'd work best.  They don't identify them by anything except number, but\ldots I think Coil was a test case.''}



I nodded.



``\emph{So were we}.''



``We had an idea,'' I said.



``\emph{Yeah.  But there's more\ldots I don't know how much more.  Yet.  Can you flip ahead?  Maybe about three quarters of the way through, there should be a bit about the Overseers and the Terminus.  Flip through\ldots slower\ldots show more of the pages\ldots I'll go back through the video feed to view each page on my own and figure the rest out myself.}''



Further down the hallway, Shadow Stalker stepped out of a room.  I looked, keeping my head at the same general angle, so the camera would continue to have a view of the book, still flipping.



Shadow Stalker was pointing.



My swarm caught up with her, flowing into the room.



I glanced into the room as we passed.  Two more bodies.  Two men, large, both bristling with horns.  One with curling horns like a ram, the other with horns like a bull.



``\emph{Satyr},'' Tattletale confirmed.  ``\emph{Again.}''



``Hmm,'' Shadow Stalker murmured.  She was leaning against the doorframe, her arms folded.  ``He's efficient.''



\emph{Did she just sound like she was approving}?  I lowered the booklet, raising my head to give Shadow Stalker a serious look.



She only made a small, smug sound, like she was pleased, or \emph{pleased with herself}, and then turned around, her cloak flaring out before she disappeared through the wall.



``This long-delayed revenge thing is getting easier all the time,'' Imp commented.



``No revenge,'' I said.  ``Not to put too fine a point on it, but you're sounding a lot less like Imp and a whole lot like\ldots well\ldots''



``Regent,'' she said.



I nodded.  The desire for revenge, the way the wisecracking was veering off course, to uncomfortable or dangerous levels\ldots



``Be nice if he was here,'' was all she said.



I nodded again.



The hallway reached a t-junction at the end, with a path going off to the left, and a stairwell to the right that led down, deeper into the building.  I could sense just how thick the floor was.  Most buildings had only a few feet separating each story, but here, there was solid matter nearly as thick as the open spaces.



\emph{A fortress?  A fortress has soldiers.}



A shelter?  It doesn't make sense that they'd try to take shelter in a place like this\emph{.}



It also made the descent to the next floor down take just long enough that it felt like something was wrong.  Winding our way down.



\emph{``There are backup plans if the whole parahumans-as-leaders thing didn't work out.  Brainwashing leaders like they brainwashed the case fifty-threes.  So the leaders were absolute and could be trusted.  Um.  Distribution and organization for getting things going again, depending on how many threats remain after we make it through this.  They didn't know }\emph{what the end would be like, what we'd be up against, so they could only ballpark here.  The reason for these offices?  Cauldron's going to staff this place.  It's going to be a hub, police, a whole lot more, up until humanity's got the ball rolling again.}''



``No way that doesn't fall apart,'' Golem said.



I nodded a little.



``Power fucks everything up, doesn't it?'' he asked.



``Speaking of fucked up.  You should know, Scion just hit Dalet.  It's ugly.  Getting worse with every attack.  A little more ruthless, toying with specific people, breaking them before he obliterates their friends.  He's going to hit our settlement again if the pattern holds.  Within the next half an hour to an hour.''



I sighed.  Nothing we could do but hope the defenders could hold their own.  I looked at Lung.



``What?'' he asked.



``You wanted to come with us.  Odd choice.''



``I tried, I did nothing in the end.  I do not like being\ldots''



``Impotent?'' Imp offered.



Lung growled his response, ``A mere bystander.''



We reached a set of double doors.  A foot thick, solid, they overlapped rather than meet, effectively doubling the thickness, allowing for their structure to reinforce one another.  They'd been destroyed, pried apart.  An impressive feat, considering they looked like they were meant to withstand charging elephants.



Or parahumans.



\emph{It's a prison}, the thought struck me, as we passed through, getting a glimpse of the floor below.



Rows and columns of cells, connected in strings of ten or so.  Most cells were occupied.



Not case fifty-threes, going by what my bugs told me.  The case fifty-threes were the outliers, here.  These were people who I might have seen on the street in Brockton Bay, all in matching outfits.  Men, women, children.  All young, twenty-five or younger.  All more or less in good health, if a touch thin.  My swarm touched each of them as I tried to take in their total numbers.



``They're here!''  Someone called out.



\emph{They can't see us from this angle}, I thought.



Then it dawned on me that everyone here had powers.  Some had powers that would sense us.



``Did it work?'' the person from before called out, a woman.  ``Hey!  Did it work?''



``They aren't the same people as before,'' a man said.



We needed to move on.  The double doors leading down to the next flight had been torn apart as well, and that meant the Irregulars, Revel, Exalt, Vantage and quite possibly the Doctor were all downstairs.



But the noise level increased with every passing second.  Cheering, shouts, cries, even threats to urge us to move faster, in a dozen different languages, maybe more.  The noise swelled as others took up the cry.  People screaming at the tops of their lungs.



And they were threatening to draw attention to us in the process.  I drew on my relay bugs, sending the swarm downstairs, trying to figure out if we'd just alerted Weld and the others.



``They think we're here to rescue them,'' Golem said.



``Aren't we?'' Cuff asked.  ``I mean, it's not why we came, but we can't leave without them.  We're not heartless?''



That she made it a question was telling.



That she directed that question at \emph{me} was\ldots I didn't even have the words to articulate it.



``Yes,'' I said.  ``Yes, of \emph{course}.''



``If we rescue them, then it causes trouble.  Too many to look after,'' Lung said.



``Chaos could help us,'' Shadow Stalker observed.



``We \emph{are} going to rescue them,'' I said.  ``It's just a question of when.  And how.''



I walked forward until I could see the cells and their occupants.



Hundreds of cells, and there wasn't anything blocking them off.  Open doors, with nothing visible that would keep the prisoners inside.  Most consisted of only three walls and a white line painted on the floor.  Beside each cell was a metal plate, engraved with a number.



``Oh my god,'' Cuff's voice was touched with quiet horror, almost lost in the rising noise.  ``Look at how pale they are.  They've been here a long time.''



``\emph{These guys haven't been here for long},'' Tattletale said.  ``\emph{Or they're the newest.  Two thousand and fifty cells, I'm thinking, maybe half of them occupied.  All the structural reinforcements, the heavy doors, the traps in the ceiling, it's to keep the prisoners in.  But you don't need to put security doors in for going downstairs if there's no way out.  There's more cells downstairs, with older patients.  Plus, I think, the hub of Cauldron's operation.}''



``This can't be for humanity's sake,'' Golem said.



``\emph{It is},'' Tattletale said.  ``\emph{Everything they've been doing is for our sake.  Producing better formulas to get more soldiers for the biggest, most important fights, weaning out the bad formulas so nobody important gets them\ldots}''



``And the case fifty-threes?'' I asked.  ``Dismissed as bad formulas?''



``\emph{At first, maybe.  But there's a use to them.  As a rule, they're stronger, tougher.  If we're forced to make a break for it, scatter humanity and survive with the remnants, the case fifty-threes can settle places you or I couldn't.  I think there's something else, but I don't see it\ldots lemme keep looking.  There's got to be a hint.  Might have to get you to run upstairs to fetch a file or something\ldots}''



Tattletale trailed off, going silent but for the occasional mumble.



Was \emph{this} the army that Cauldron wanted to deploy?  Men and women with powers they didn't ask for, released with stipulations, or simply deposited on a battlefield and left to fight or run?



It felt too thin.  Even this many capes, they were untrained, their powers presumably unpracticed.  They wouldn't amount to more than cannon fodder.



I stopped, feeling the scale of it all.  Hundreds of cells, hundreds of \emph{voices}\ldots



``Quiet!''  I called out.



My voice was lost in the noise.



``\emph{Quiet!}''  I used my swarm to transmit my voice.



Some listened, as if waiting for me to say something else.



I wasn't sure what I could say.  I glanced at my teammates, searching for an idea, before something came to me.  ``\emph{Save your energy.  Don't exhaust yourselves shouting.}''



They listened, quieting down.  At first.



But excitement won over.  There was no way to communicate their excitement other than by talking to their cellmates, or the people in cells across from them, but as the general volume rose, they had to raise their voices to be heard.  It didn't help that the entire area was a giant acoustic sounding board.



``I could sing,'' Canary said, raising her voice to be heard, ``But I think I'd calm you guys down too.''



Rachel whistled, a shrill sound that almost made my \emph{bugs} wince in pain.  Not a soothing song.



In the silence that followed, Bastard shook his head a little, then snapped at open air.  Too sharp for his wolf senses?



``Good,'' Lung said.  Rachel only scowled at his approval.  He added, ``You have to follow this with something that drives the point home.''



``Make them fear us?'' I asked.  I remembered Bakuda's commentary on her lessons from Lung.



``Fear?  \emph{Respect,'' }Lung said.



``Same thing,'' Shadow Stalker said.



Lung shrugged.



I didn't feel like arguing the point, and the crowd was very patiently waiting.  They were barely making a sound now.



Which was good, but was there any guarantee they wouldn't get riled up as we made our way down to the next floor?



Bastard shook his head again.  Rachel and I both looked at the same time, then made eye contact.



I spread my bugs out through the area.  Felt the Custodian flowing through the air, a little faster than before.



She flew towards me, and I flinched, taking a step back.



She repeated the process, looping back, then charging me.



This time, when I took a step back, it was on purpose.  She'd done it a second time because she wanted me to take a second step.  And a third, a fourth\ldots



``Go,'' I said.  ``This way.  \emph{Move.}''



We ran.  I focused on my swarm, spreading the bugs out as much as I could behind us and in front of us.



Different cells sat at the end of the hallway.  Bigger cells, arranged so that they faced the opposite direction, with paths leading in, then to the right, then back into the room.



Two-nine-three.  An empty, unlabeled cell.  Two-six-five.  Two more empty, unlabeled cells.



Bastard shook his head again, opened his mouth in an almost yawning, lazy bite.  I could sense the Custodian there, brushing by the side of his face.



I moved the swarm to block the other inmate's view of us.



``Head--'' I started, but Rachel was already making her way inside one of the empty cells.  She'd put the pieces together.  ``\ldotsright.''



I hung back, looking over my shoulder as the others filed into the cells.  I hurried down the hallway, then kicked the door.  I saw a glimpse of a stairwell, identical to the one we'd used at the far end of the room.



I reversed direction, then ducked into the same corridor the others had entered.  Let the people nearby think we'd left.



I wasn't sure it was the brightest thing, taking the dead end over the open-ended exit.  But the Custodian had suggested this.



I felt a moment's trepidation.  \emph{Why}?



``\emph{You're being followed,}'' Tattletale said.



I shook my head a little.  I could sense my bugs.  Nothing.



Was it a trap?  Would the Custodian shut some kind of door on us, locking us within?



No.  She had no reason to.  As hard to define as she was.



I pulled the camera free from my mask, then pressed it against the side of the mount on the cell exterior that would have held a number plate.  I ducked inside.



``Tattletale?''



``\emph{I get it, I get it}.  \emph{Might need to ask for help on this one.  Sit tight.}''



The cell was empty, but it featured a double bed, a television, a computer, a small bookshelf of cases with stuff to watch or play, and an odd little double-layered glass window that looked out onto a wall of gravel.



I joined the others, drawing my phone from my pocket.  It took a moment for Tattletale to manage the link-up.



``\emph{And you've got video.  I'm brilliant.  Admit it.}''



``You're brilliant,'' I said.



If I'd had the idea earlier, I would have wound up with a better vantage point.  As it was, we viewed the scene from a distance.  I held the phone flat, so our group could circle around to observe from different angles.



The noise of the crowd became a roar, muffled to near-silence by the cell's walls.  The occupants wouldn't have heard the other prisoners, except in the most extreme cases.  I could see the Irregulars as they entered from the same direction we had.  I could see the crowd that followed the Irregulars.



Case fifty-threes.  Kind of?



No.  Different.  The way they spread out, their haggard appearances, they made for the best clues when these individuals were just silhouettes seen from three hundred feet away.  But they got closer, and I could see how they differed.  They didn't take on the traits of animals, nor simple mutations or exaggerations in features.  There was a man that burned, who staggered forward, like it \emph{hurt}, but he wasn't consumed.  A woman who floated, every part of her body a distinct piece, separated by open space.  It made her look twice as tall.  A\ldots \emph{something} that inched forward, occasionally running to keep up with the crowd.  Hands and feet like flippers, but the face was an orifice, and thin worms were spilling out, swarming over the surface of his body in numbers so thick that the flesh underneath was impossible to see.



Case fifty-threes that Cauldron had kept in reserve, it seemed.  I could see the anger in them, the tension, the wariness that came with what had to have been\ldots how long?  With the hair, the beards, maybe \emph{years} of confinement.  Maybe even \emph{solitary} confinement.



\emph{On camera}, I could see this.



I couldn't feel them with my bugs.  Couldn't see them, couldn't hear them.  A revised image, an edited image, as if the whole crowd had erased with some careful photo editing.  Sound editing.  Touch editing?



``\emph{Oh, hey,}'' Tattletale said.  ``\emph{Anyone else having trouble getting a read on those guys?}''



``I am telling myself we may fight soon,'' Lung rumbled, ``But my power is not responding as well as it should.  Looking at them, seeing what look to be worthy opponents with little to lose, I should be feeling it build faster, a pressure inside me.''



``I can't see or hear them with my bugs, let alone touch them,'' I told Tattletale.



``\emph{Over an entire area.  Mantellum,}'' Tattletale said.  ``\emph{The guy with the built-in cloak, dead center.}''



I looked, but the crowd moved.



They were talking.  We didn't have audio.  There was only the rise and fall of the crowd's shouts, letting us know when people were talking and when they were reacting to statements.



On camera, people began to leave cells.



``\emph{It's a power with layers.  Each successive layer enhances the level of protection.  Except everything on record says the range it blocks powers only extends about fifteen feet.  Get within five feet, no senses work.  It's not supposed to be a hundred feet like this.}''



``Six times the range,'' Cuff said.



``\emph{Somehow.}''



I pursed my lips.  ``The Doctor?''



``\emph{Probably downstairs.  Look at the way the group at the rear is set up.  They're watching to make sure nobody comes upstairs.  I think they have the Doctor trapped down there.}''



\emph{They have us trapped here too.}



I didn't say it out loud.  Canary looked scared, and both Lung and Rachel looked restless.



``\emph{There's this guy that looks like he's in charge.  You see him}?''



It was a voice over the earbuds, but it wasn't Tattletale.



``\emph{You're an idiot},'' Tattletale said.  ``\emph{I love you for this, but you're an idiot}.''



``Who?''  I asked.



``\emph{Imp},'' Tattletale said.



Imp?  It took me a second.



Imp.  Damn it.  Grue would kill me.  She was close enough to overhear, and this many parahumans\ldots so many ways she could be detected.



``Mister beautiful\emph{,}'' Imp said.  ``He's saying they're free\ldots oh, whoop.  Here we go.''



The cells emptied.  It was almost like the order being given was a stone dropped on the water's surface, the movement of the cell's occupants the ripple, the ones who didn't hear the man speak reacted to the others' movement, and the chain reaction continued.  Hundreds of people.



Hundreds of \emph{victims}.



The roar of the crowd increased in volume.  I could feel the \emph{floor} vibrating.  No power at work.  Just a \emph{lot} of people, stomping and cheering.



The Custodian moved a little, then stopped.  I could sense her more than before, a disturbance, agitated.



She was the one that had been enforcing the peace, keeping people contained in cells without doors.  Now\ldots either Mantellum or the strange case fifty-threes were keeping her at bay, preventing her from seeing to her duties.



The lights flickered, a little worse than before.



``They're going to come here,'' Shadow Stalker said.  ``I spent time in juvie, if someone had a nice \emph{toothbrush}, cookies from mom, there was jealousy, retaliation.''



I nodded a little.



And a cushy cell like this\ldots



``They will come,'' Lung said.  The irises of his eyes were orange, and hive-like lumps were standing out on his skin, where scales threatened to push forth.  ``I can win, but you will all most likely die in the time I require.''



``\emph{I need all the people who can bore through solid steel}, he says,'' Imp spoke over the comms.



``Lung's plan can be plan A.  Let's hear plan B,'' I said.



``We run,'' Shadow Stalker said.  ``Door's right there.''



``I could make barriers,'' Golem said.



The roaring dimmed.  The man was speaking.  The cupboard door beneath the large television seemed to rattle with \emph{more} intensity.



``Custodian says\ldots door?''



She stopped.



``\emph{Barriers},'' Tattletale said.  ``\emph{We'd have to get past more security doors, ones the Irregulars haven't dealt with.  Quite probably other security measures.}''



Imp spoke up, ``Pretty \emph{guy's saying\ldots traitors to our kind.  See they get the justice they deserve.  Oh\ldots hey.}''



I looked at the phone.



Weld, mangled to the point that he looked more like scrap metal than a person, was heaved forward, thrown to the ground.



A sphere rolled forward.  Something coiled within, behind the colored transparent pane.  Someone in the crowd grabbed it, then made their hands glow.  Fire?  Heating the material?  I couldn't tell from this distance, but I could see the movement within accelerate in fits and starts.



Weld reached out for the sphere, but his arm was so badly damaged it couldn't hold his weight.  It bent the wrong way, breaking off.  When he rolled over onto his back, the forearm was stuck to his upper arm, hand to his shoulder and neck.



If he'd been a human, if \emph{half} that much damage had been done, there would be no way he'd be alive.



``Doesn't get much worse than a crowd this mad,'' Shadow Stalker said, her voice low.  ``I can probably make a break for it and get away.  Not usually my thing to be nice, but\ldots you want me to pass on any messages?  Last words?  My memory is shit, but I can try.''



The crowd was reacting, the contents of the room shaking with the sound.  Out there, it would be deafening.



Then they\emph{ moved}.  People were parting the way.  Opening a path to our end of the hallway.



The camera gave us a view of the central gang.  A spiky boy with yellow skin.  A man with exaggerated masculine and feminine features, a caricature, burdened with muscle.  There was Gully, the muscular girl with the shovel, braids and severe overbite who'd helped out against Echidna, looking ill at ease.  A boy with red skin.  Sanguine.



As they got closer, I could feel my power changing, to tell a lie.  No people in the area.  A conspicuous clearing in the gap.  There were enough people to push my insects around, wherever they were, but my brain was revising it to make sense of the scene.  It was unusual enough to grab my attention, though, but not accurate enough for me to use it.



``Feel up to singing?'' I asked Canary.



``They'd hurt me before I got anywhere,'' she said.  ``Probably.  I'll try.''



I closed my eyes.  I could feel my swarm out there, both inside and outside of Mantellum's power, but I couldn't do anything meaningful to the crowd with it.



``Satyrical's out there,'' I said.  ``His people\ldots''



Tattletale spoke.  ``\emph{Probably happen to be the ones who stayed behind to dig for the Doctor.  Nobody there, in Satyrical's group who're going to be able to deal with this mob.  Probably nobody in the Doctor's group, either.}''



I nodded, drawing my knife.  The one Defiant had given me.



Not enough to cut our way to freedom.  Judging by the gravel outside the double-pane window, we were sitting beside layers of rock.  The knife could get us into the next cell, maybe the cell next to that\ldots but it wouldn't let us get anywhere fast enough to outpace the crowd.



``Plan A, then,'' Lung spoke, somber.  ``For your sacrifice, I will grant you a favor.  Tell me if you want me to kill someone, an enemy you want gone.''



``We're \emph{not} going to die,'' I growled the words.  I began forming the swarm into a decoy.



A distraction.  If I could get the crowd's attention, lead them upstairs-



The pretty man outside spoke, and I could see his lips move on the camera.  There was no need for translation.



\emph{Revenge}.



This time, the jeering was just outside our cell.  The mob advanced.





