





Prisoners and case fifty-threes flooded into the narrow corridors, making their way into the special cells.



I gestured, urging others to move.  They shifted until their backs were against the wall.  Golem and Cuff even stepped onto the bed, to get out of the way.



I found myself by the door.  Mantellum wasn't close enough to blind my bugs, so I could track the people as they came around the corner, approaching the doorway.  A gang of them.



I drew my second knife, then activated the knife Defiant had given me.  Safety\ldots and the trigger.



\emph{One\ldots two\ldots}



The guy at the head of the group made it into the doorway.  He stopped as he saw Bastard.  I pressed my old knife's blade against his throat, saw him back away, only to bump into the people behind him.



\emph{three\ldots fo-}



The knife finished forming the gray blur around it.  Roughly three point seven seconds.  Good.



He didn't look worried.  So I reached out and dragged the blur against the wall, gouging out a groove a few inches deep.  Smoke expanded.



He froze, his eyes flicking down, as if he could see past his cheekbones, face and chin to the knife I had against his throat.



I nodded slowly.



``Move it, asshole!''  one of the captives said.



He didn't move.  I saw his eye shift, until it settled on me.  My arm moved, not wholly steady when fully extended, a weight in hand, and I felt the blade rasp against the scruff on his neck.



Not a case fifty-three.  Just an ordinary guy.



`Ordinary'.  He was here, he would have powers.



``Move!'' the guy in the hallway ordered.



``\emph{Dim byd yma,'' }my hostage said, without breaking eye contact with me.  Then he added, in a heavily accented voice, ``Is nothing here.''



The cheering reached a climax outside.  My bugs could sense the people in an adjacent cell.  They had someone, and were dragging him out as a group.



``Something's going on,'' one of the guys in the corridor said.



``Don't care.  \emph{Move}, motherfucker.  I want to see if there's any shit in there.''



``Is no shit,'' my hostage said.  ``Empty.''



I nodded slowly.  Oddly enough, he looked \emph{more} concerned at that.



An issue in translation?  A cultural problem?



The roaring reached a climax.  They had a man with no arms or legs, not fat, but with a goiter-like mass around his neck\ldots hairless.  A case fifty-three.



``\emph{This one,'' }Imp said, repeating what the mob's ringleader was saying.  \emph{Shouting}, judging by the way he was acting on camera. \emph{ ``This traitor, he is how they controlled us.  How they planned to control you.  He was going to brainwash these ones into a private army\ldots he's pointing at the weird looking ones they brought from downstairs.  This traitor was going to send the rest of you out without any memories, without identities, as Cauldron's trash.}''



``We're missing it,'' the one further down the corridor said.



\emph{It's only the three, now.  The rest backed out to check out the scene.}



``I think I know what we're missing.  It's not worth seeing.  But first dibs at whatever's in this cell?  If this fuckhole doesn't move out of the doorway, I'm going to slide a foot up his rectum, and pry open a \emph{new} doorway.''



I glanced around the room.  I could see how tense the others were.  Even Lung was rigid, bristling with scale-points.  Primed for a fight.



Imp's voice came over the earbuds.  ``Oh, hey, fun fact.  You can apparently crucify someone without arms or legs, if you try hard enough, and have the right powers.  He's getting the crowd worked up, trying to start up a witch hunt.  Um.  He's shouting, who wants to kill the real monster, the monster who did this to us?



The bloodthirsty cries of the crowd made it through even the soundproofing of the cell.  I could sense the emotion, the anger.



``\emph{Look to your neighbors, the ones next to you.  Are they shouting loud enough?  Are they angry enough?  Because we aren't going to brook any traitors.}''



My hostage looked like he was going to have a heart attack.  Caught between two very dangerous people.



I relented, easing up on the knife, then I beckoned for him to enter the room.



Slowly, he obeyed.



The guy behind him spat.  ``Fucking liar.  I \emph{knew} you were lying.  Trying to keep all this shit to your\ldots self\ldots''



He trailed off as he got far enough into the room to see me and the others.



I gave my hostage a push, with the idea that he'd get put off balance for the others to deal with.  Except I failed, completely and utterly, to budge him.  He started to turn, and I left him behind, hurrying forward to slide behind the second man and confront the third before he could catch on to what was happening and alert others.



The others folded in on the first two.



I could see the third man's eyes go wide as I approached, my bugs swarming.  I had a knife in each hand.



He had other powers.



\emph{Fighting capes I don't know, unfamiliar powers}.



A sphere of light surrounded my right hand and knife, more spheres lighting up to surround the largest clusters of my swarm, turning each of them into fireflies in the darkness.



Which put me in the awkward position of figuring out what his power did and counteracting it.  The obvious solution, a solution to \emph{most} powers, was to hit him before he could hit me with whatever it was he did.



I tried moving bugs outside of the sphere, and the sphere moved with them.  I moved individual bugs in different directions, and I felt them distort, coming to pieces, as if they were blobs of ink and I was pushing them against a hard surface.



Bugs made it through his perimeter, biting and stinging, and he reacted with the appropriate pain.  But the bugs surrounded by light \emph{didn't} manage to bite into flesh.  They were soft, their mandibles bending like putty.  Where he swatted his hand against them, both spheres and bugs were distorted and crushed by the movement.



I moved the bug-spheres out of the way, thrusting with the knife-hand he hadn't yet affected, to cut off his retreat.  I felt the effect surround it as I got closer.  Another sphere.



I pulled back, instead.  I moved my body to block his retreat, and then drove my knee into his stomach.



He staggered back, then cast out more lights, surrounding my elbows, knees\ldots



My head, too.  My vision went\ldots not blurry, but the colors smudged, like bad watercoloring.



Breathing became more difficult.  Not impossible, but difficult.



The bugs who'd bent their mandibles or distorted in the course of making their way outside of the spheres weren't going back to normal.  I wasn't sure I wanted to hit this guy with any of my body parts, if they wouldn't bounce back to their normal shape after the fact.



I wasn't sure I wanted him to hit me, either.  If my face proved that pliable and he punched it\ldots



He charged me, and I was forced to move out of the way.  He stumbled for the other end of the corridor and for the crowd, a hand pressed to his stomach.  I unspooled lengths of silk cord from the dispensers at my belt and beneath my armor, dragonflies lancing past him to encircle his throat and feet.



I braced myself, ready to try and arrest his forward momentum, but one of the threads was shorter than the others, and he only tripped.  He glanced over his shoulder, then cast out his spheres, so they covered my feet.



I threw myself forward, my flight pack kicking into action.  I lost my orientation, fighting to activate the individual panels in such a way that my hands, feet or head wouldn't slam into a wall.



Imp said something, reciting a comment, but my focus was elsewhere.



The flight pack cracked against a wall, and I came to a dead stop.  For long seconds, the two of us were stuck.  I was unable to walk, because my own body weight would crush my feet, with this softening effect.  I couldn't touch anything without turning my hand or whatever into mashed potatoes.



For his part, the guy was caught on the ground, his feet bound by cords too thick and strong to break with his own raw strength.



The lights flickered  out.  I could see him using his power.  An orb of light, surrounding a length of the thread.  He could counter that, while I wasn't so lucky as to be able to counter him.  He pulled his legs apart until the thread had stretched out to the point of snapping.



He started to climb to his feet, finding other threads and using his power to break them.  He was screaming, but nobody seemed to hear him over the noise of the crowd, and all eyes were on whatever was going on in the Mantellum blind spot.  He wasn't getting any help, but I couldn't stop him.



Not with the thread.



So I controlled the swarm, driving bugs into his nose and mouth.



\emph{You want to play hardball, Softball}?



He collapsed, choking.  Some would have capsaicin, but few of the laced insects would be alive, covered in hairspray and a toxic chemical, so long after I'd last refreshed them.



Slowly, in the order he'd created them, the spheres disappeared.



``Need help?'' Cuff asked.



``No,'' I said.  \emph{Forty seconds ago, yes.  Not now}.



``Right,'' she said.  She looked at the choking man.  Her voice was a little different as she said, ``Okay.''



When the spheres around my feet and hands had faded, I let myself drift to the ground.  I hit the safety and trigger to remove the blur, then sheathed my knives.  Once my hands were free, I clenched and unclenched my hands to make sure everything was in working order, and then grabbed the threads that still remained.  I pulled on the threads until he was in a position where Cuff and I could get our hands on him and drag him back towards the others.



There were cheers.  I looked at my phone, and I could see the weirdly pretty man.  Chains stretched out from the armless, legless figure's stumps, extending to the high ceiling and the floor, suspending him fifteen or so feet in the air.  Dead, or close enough it barely mattered.



I could also make out Mantellum, at the center of the crowd.  He stood beneath the guy they'd strung up, blood running off of the shroud that seemed to flow from his back and the edges of his face.  His expression was hard to read, but the fact that he seemed to be luxuriating in the blood rather than avoiding it\ldots it didn't put him in my good books.



``\emph{It looks like we've got a full-on riot here},'' Imp commented.  ``\emph{Armless dude's good as dead, they're splitting up the crowd, so anyone that's not inside the circle has a few guys who can deal with the ghost janitor.''}



\emph{``The Custodian,'' }I said, as I rounded the corner.  I shoved the still-choking prisoner to the ground.  The one I'd held hostage was pinned to the wall, arms and legs held fast to the surface by Golem's projected arms and legs.  Lung stood with his face just a foot away from the man's.  Bastard stood with his paw on the chest of the remaining prisoner.



Three dealt with, no alert given.



The pretty man and the spiky, yellow guy were holding a prisoner's hands up the air between them, like they were celebrating a prize fighter.  I could hear the noise of the crowd, as if it were far more distant than it was.  My \emph{bugs, }outside of Mantellum's effect, could hear it at full force.



``\emph{Her.  Right,'' }Imp said. \emph{ ``He's getting them hyped, saying they're going after the Doctor, but they need to dig.  Picking out the people who have the best powers for the job.  They're shouting out what they can do.  I think they're leaving soon.}''



The small army we were faced with aside, I found myself smiling a little behind my mask.  The situation evoked memories.  Except this time, I had a cell phone.  I had the pepper spray.  I had a weapon.



I'd changed.  I was more prepared to do what needed to be done.



``Less to fight,'' Lung said.  ``If you are scared, children, you can stay here.  In a moment, I will go.''



Taunting?  Mocking?  No.  Not really his style.  Confident in his superiority, now that he'd changed as much as he had.  Not \emph{full} changes, not even full coverage with his scales, but he seemed to think he could throw himself into the crowd just outside the corridor and survive.



``We should exfiltrate,'' Golem said.  ``Lose the costumes, wear other ones, blend into the crowd.''



``Except you need your costume,'' I said.  ``Cuff's far stronger with hers.  Imp, Rachel and I benefit pretty heavily from ours.''



``It's just an idea,'' Golem said.



``It's an idea,'' I said.  ``Very workable, but it doesn't address our main issue.  We need to stop them from going after the Doctor.  If we only wanted to escape, then I'd agree with your plan, but for now--''



``\emph{Looks like they have groups formed},'' Imp said.



It was true.  I had to tilt my phone so others could see what I was seeing.  Gaps had formed between the discrete groups, as everyone figured out who they were sticking with.  The main group looked like it had eighty or ninety people.



``That's a lot of people to stop,'' Golem commented.  He gave me a sidelong glance.  ``You're wanting to do something here?''



I nodded.  ``Have to, don't we?''



``Damn it,'' he said, but he didn't argue.



``Canary?'' I asked.



Her eyes were on the two guys we had on the ground.



``Canary,'' I said, a little louder.



Nothing.



One was still choking.  I ordered the bugs to make their way out of his airway.  They weren't \emph{blocking} it, but they were keeping him down.  We had the situation here under control.



Canary didn't seem to relax any as the bugs flowed out of his mouth and nose.  A few crawled forth from beneath his eyelids.  He coughed and gagged.



She got \emph{more} tense as I let up on `softball'.  Maybe I should have left him the way he was.



``\emph{Canary,'' }I repeated myself for the third time, injecting a little more force into my voice.



She looked at me, disoriented.



``Can you sing to them?''



``Just them?''



``If you don't have control, then yeah.  Just them.''



``I guess.''



``It makes them suggestible?''  I asked.



``I don't really know.  I never really experimented with my power.''



``Not even in the Birdcage?''



``Not really, no.''



I nodded.



``They'll listen to me.  If I really get into it, they'll do anything I say.''



``Are they suggestible to you alone, or \emph{everyone}?''



Canary shook her head.



``You don't know,'' I said, in the same instant she said, ``I don't know.''



``Can you group them all together?''  I asked.



Lung moved fast enough that it caught me off guard, bending down to grab `softball' and the other guy by the throats.  He slammed them against the wall, putting them beside the guy I'd taken hostage.



Golem bound them in place.



Lung grunted, and I couldn't read any meaning in the noise.  Irritation?  Satisfaction?



He was restless.  Ready for a fight.  The sound might have been a `there, now we can stop talking and do something.'



``Lung,'' I said.



``Mm?''



``Go watch the corridor?  Your hearing is good enough you can follow along.  Plus you might not want to be too close to Canary, here.''



``Mm,'' he said.



\emph{Less verbal, now, because of the transformation?}



Canary crossed the room, and she began singing.  Wordless at first, as if sounding out what she wanted to do, then with more character.



Even though she kept her voice low, it still reached me, and that made me more than a little paranoid.



I moved to the other end of the cell, leaning against the wall.  When I could still hear the sounds, I put a curtain of bugs between myself and her, and made them buzz and drone, fluctuating the sound until I couldn't make out what she was doing.



``What are you thinking?'' Rachel asked me.



``Chaos,'' I said.  ``Ideal world, it won't be chaos with \emph{us} at the center.''



Rachel nodded.  ``No dogs, then?''



That many parahumans, I suspected the dogs wouldn't last more than a few minutes.  ``No.  Let's not put them in too much danger.''



``Lovely sentiment,'' Shadow Stalker said, just a little sarcastically.  ``So how are you pulling off this chaos thing?''



``\emph{Whatever you're going to do, do it soon},'' Tattletale said.



I gathered my swarm into a cluster.  Then I activated my knife.



Using thread, I bound the knife handle, then lifted the knife into the air.



``What are you doing?'' Cuff asked.  She sounded genuinely curious.



The bugs stopped working to carry the knife, and I very carefully grabbed it by the handle, before withdrawing my hand from the mass.



``Had a thought, but it doesn't work.  It's too conspicuous, the swarm.''



``Floating death knife?'' Shadow Stalker asked.



``That was the basic idea.  But I'll need to do something else,'' I said.  I turned off the effect around it, watched as it dissolved into smoke.  ``Custodian.''



I felt out with my bugs.  She reached directly into the swarm, letting me feel the slow movement of her hand.



``Generally speaking, you think you could handle most of the ones out there?''



She slowly floated through my swarm.  The movement of her head\ldots was she shaking it?



I felt a familiar kind of disappointment.  We had the tools.  Canary's song, Lung, the knife, the dogs, the Custodian, my swarm\ldots but in execution, it didn't fit together.



The crowd was stomping now, a rhythmic stomping, the crowd working in unison.



If anyone wasn't game, if anyone \emph{wasn't} keen on the lynching of the armless man, they had to be powerless in the face of this much fury.  How could they speak against it?  Defend the man?



It was scary to think about.



``\emph{Riling them up to go trash the place},'' Tattletale said.



There was a crash.  I turned to my cell phone.  A cloud of dust, the crowd was agitated.  Someone had trashed a cell, or a group of cells.



``\ldots\emph{If they keep doing that, they're going to hit these cells awfully soon},'' Tattletale added.



I shut my eyes.



``We'll have to give it a shot,'' I said.  ``Shadow Stalker?  Leave.''



``Leave?''  Shadow Stalker asked.



``Find a vantage point, away from the crowd.  Be ready.  Your targets are the special case fifty-threes.  When I give you the signal, take out as many as you can.  As many as you \emph{safely} can.''



``Your concern for my well being is touching, Hebert,'' she said.



``I'd be annoyed if you got killed,'' I said.  ``I'd have that nagging doubt in the back of my mind, wondering if I sent you off into a suicidal situation because of our history.  And because we can't afford to lose \emph{anyone}.  Because you're a human, and I don't want people on our side to die needlessly.''



``So it's about pride,'' she said.  ``Petty, stupid pride, that you think the outcome of this shit is up to you.  And maybe fear?  That you'll lose too many good soldiers?''



``Whatever,'' I said.  ``However you want to interpret it.''



``I'm assuming you'll insist on tranquilizer bolts,'' she said.  ``Because you don't want anyone dying needlessly?''



``No,'' I said.  I thought of Newter, of the unique physiology of the case fifty-threes.  ``Lethal shots.''



She made a funny little laugh as she looked down at her crossbow.  She began loading it with expert, practiced movements.  ``Funny how it all turns out.  \emph{This}, for one thing.  That I can't anticipate you anymore.  And\ldots that it's just you.  There's nobody to mourn me when I'm gone.  Family doesn't really care.  No friends left.  No teammates, even.  I'm left to console myself with the idea that, if I die, I'll at least \emph{annoy} the depressing, creepy little geek from high school.''



``I'd say something reassuring,'' I said.  ``I want to tell you that you matter more to me than that.  Or that I'm sure you matter to someone out there\ldots but I don't think you'd buy it.''



``I wouldn't,'' she said.  She wasn't maintaining eye contact.  ``Whatever.  I'm going as far up the stairs as I can, put myself half out the wall, snipe from there.  I'll be a minute.''



Then she was gone, stepping through the wall, heading towards the stairwell closest to us.



``\emph{You meant that shit, Skitter?}''  Imp asked.  ``Wanting to care?  Wanting to reassure her?''



``Pretty much,'' I said.  ``At this juncture, there's no reason to lie.''



``\emph{You're too forgiving},'' she said.



The lights flickered as another impact shook the complex.



``\emph{They're going}.''



``So are we,'' I said.  ``Just as soon as Canary's ready.''



Imp spoke, ``\emph{Always ticked Alec off, you know.  That you weren't any good at holding grudges.  Too focused on the present, when it came to picking your enemies and your allies.  I wound up defending you, even.}''



I was barely listening, trying to focus on the swarm, picking out the places they could operate and the places they couldn't, tracking the various prisoners as they started moving.



But that last sentence caught me off guard.  ``You defended me?''



``For him, it's his \emph{raisin }\emph{de enter.}''



``\emph{Raison d'etre},'' Tattletale clarified.



``\emph{Yeah.  That.  His daddy fucked him up, so it sort of gave him an inner fire where he didn't have much more than coal inside, y'know what I mean?  Forward momentum, itch to go out and get shit done?  Become a villain with the idea that maybe someday he'd get to pull one over on the old man, become a warlord.  So for him, it was the only reason he really got up in the morning, besides maybe the basic pleasures of life.  My parents fucked me over too, but it was different.  No grudge here, just a whole lot of sad.''}



``Yeah,'' I said.  I wasn't sure what to add to that.



``\emph{So it was a fight.  Closest to a fight as I ever got with that asshole.  Well, if Skitter's being nice, so will I.}\emph{Good deed of the day, since I'm dicking around now, nothing to report\ldots}  You listening in, Shady?''



``\emph{Shady}?''



Man, it was eerie to recognize Sophia's voice over the earbud.



``\emph{I'll take that as a yes.}\emph{Regent told me about his stunt.  Controlling you.}''



Canary passed through my swarm.  She was silent, and the glances to the side when Imp was speaking suggested she didn't want to interrupt.



``\emph{He took you home.  Gave you a hard time, messing with your mom.  The whole thing with you nearly committing suicide afterwards.}''



I was very still.  The lights flickered, the ground rumbled, and I didn't so much as flinch.



``\emph{Well, I'm not going to `prattle', as Lung would put it.  He was there, obviously.  He told me about it, after the fact.  Just, like, a heart to heart, between two of us who don't have much heart to go around, you get me?  Neither of us's the type to get embarrassed, so nothing to hide.  Can share all the stories.  Share each other, just by talking?''}



She made it sound like a question.  Like she wasn't even sure, and she wanted validation from someone.



I remembered how Regent had controlled her.  Seized her with his power.  \emph{Sharing each other indeed.}



``\emph{Not a guy that's in touch with his emotions.  Way I always saw it, they're there, he's just oblivious to it all.  Had to be.  So it's only after he's through with you that he realizes maybe he was a little hard on you, maybe he twisted the knife harder than he usually would, because it bugged him.  There you are with a family, and he can feel your emotions, and he totally knows you don't even realize it in the slightest.  He's blind to his own emotions and you're blind to the emotions of others.''}



``\emph{Is this going somewhere?}''  Shadow Stalker's voice.  ``\emph{You're prattling.}''



``\emph{Take it from me, as I tell you what the lazy jerk who body-controlled you told me.  Your mommy loves you lots, Shady.}''



There was a pause.  ``\emph{Okay.}''



``\emph{That's all you're going to give me?  I totally dish all this, and I get an `okay'?}''  Imp asked.  She was oblivious to the pause before Shadow Stalker had spoken, to the fact that she'd affected Shadow Stalker on some level.



That, or Imp's wording had taken a second to figure out.



``No arguments,'' I said, cutting in before something could start between two of our more volatile members.  ``Canary?''



``They're ready.''



``Good.  Rachel, Golem, Cuff.  If and when we move, I need you to run interference.  When we move, I need you to distract, protect the core group, protect us as we run.  Rachel, keep the dogs large enough they can maybe take a hit or two, but not so big they can't make their way into the stairwell.  Lung?''



There was no reply.  I could sense him out in the corridor, just at the corner where it looked out into the main hallway with the prisoners and other cells.  He turned in response.  He might have been able to hear me through the comm system, but he could have heard me anyways.



``\emph{I don't think he knows how to use the comm system,}'' Tattletale said.  \emph{``Or he does, but he's changed enough it's hard to do.''}



``Lung,'' I said.  ``The other three are giving us cover.  You have enough experience I'm not going to tell you what to do.  You've been at this cape thing for a decade and a bit.  So go all-in.  Or do what the other three are doing.  Your call.''



There was no reply.  Maybe he didn't understand the comm system.



``You're so calm,'' Canary said.  ``Most of you.  Lung seemed nervous.''



Lung, out in the corridor, clenched his fist.



\emph{You annoyed him, saying that}.



``I'm shaking,'' Canary said, and her strange, melodic voice gave evidence to her fear.  ``You can't tell with these gauntlets I'm wearing, but I'm shaking.''



``Okay,'' I said.  ``Don't worry.''



``I'm--'' she laughed a little, and the laugh hitched with emotion.  ``I'm- pretty worried.''



``We've been through worse.  Everyone here has been through worse.''



``That doesn't make me feel better.  It makes me feel like maybe I had the right idea, back in the beginning when I decided not to do this cape thing.  I'm going to fuck up, and the stakes are so fucking high\ldots''



``Relax,'' I said.  ``Or\ldots if that's not possible, just, um.  Tell yourself we've got your back.  None of us are about to let the newbie die.''



``That's not that reassuring,'' she said.



``It'll have to do,'' I said.  The ground was shaking, and someone was manually tearing apart a cell block just a distance away.  I could feel Mantellum retreating, the blind spot shifting.



I was just a little impatient.  We were running out of time, and I didn't even have everything in place.



I parted my swarm, giving myself a view of the three captives.



``You three,'' I said.



They raised their heads.



``\emph{Brutto tik},'' the largest one growled.



``Be quiet,'' I ordered, as authoritative as I could manage.



He clenched his teeth, lips pressed together.



\emph{Does he even realize he's obeying?}



``I'm not your enemy.  Stop treating me like an enemy and listen,'' I said.



I could see the tension slowly seep out of them.



``Nod your heads,'' I said, experimentally.



They each nodded, out of sync.



``Golem?  Release them,'' I said.



Golem created more hands, manually tearing the old ones apart.



The three stood still, looking just a little unfocused.



I turned to the largest one.  ``What are your powers?''



He looked confused.



``Tell me your powers.''



``I'm dense,'' he said.



\emph{Ah.}



I extended my disintegration knife in his direction, saw the delayed reaction, the genuine fear and concern.



I turned it around, offering him the handle.



He stared at it, still looking afraid.



``Calm down,'' I said.



He relaxed, very slowly, very visibly.



\emph{It works on involuntary reactions?}



He settled into a state that still looked ill-at-ease, but not nearly as afraid as before.



\emph{Or does it work on the voluntary, visible signs of the involuntary reactions?}



``Take it,'' I said.



He took the knife.



``Hide it.''



He hid it.



``Now don't move.  Don't be afraid.''



He went stock still.



``Um,'' Canary said.  ``A thing\ldots''



``A thing?'' I asked.



``He's not as influenced as my ex-boyfriend was, but\ldots they're very literal, about what you say.  Even like this.''



I looked at the dense man.  ``Okay.  Then--''



``You're allowed to move to breathe,'' Canary cut me off.



The man exhaled audibly.



``Now don't react,'' I told him.



Then I sent my flying bugs to him, collecting them beneath the generic uniform he wore.  They carried silk cord and wound it loosely around his legs and arms.



True to form, he didn't react.



I thought about it a bit more, and then gave him an excess of silk.  Hundreds of feet of it.



``This cell was empty, there's nothing inside except people looking for some privacy.  Make your way to an isolated spot where nobody can really see you, wait until the lights flicker out, and then use the safety on the knife.''



He looked at me as though he hadn't taken in any of it.



``My ex was like that, before went and obeyed me, without my knowledge,'' Canary said.  ``I think this guy will listen.''



``Then you're free.  Forget this.''



He left.  I looked at the remaining two.



``You two, shirts off.''



\emph{``Yes.  I like the way you think.''}



``Be quiet, Imp,'' I said.  ``We're moving, be ready.''



``\emph{And moving starts with sexy times.  Not complaining.}``



\emph{For someone who hates being ignored, she seems to demand it from others}, I thought.  ``Sit in the corridor, near where the spiky, scaled guy is now.  Tell him to come here.  If anyone comes, kiss.  Convince them they're interrupting something private, get angry.''



``I'm not comfortable with this bit,'' Cuff said.  ``It's creepy.''



``It's better than Lung having to tear people to shreds or burn them if they happen this way,'' I said.  ``I'll take creepy.''



``Okay, if I have to be specific, then I'll say it's a bit, um, \emph{rapey}.''



I frowned.



``Don't \emph{actually} kiss,'' I told the men.  ``Fake it as much as you can.''



Cuff nodded.



The others were all moving, now.



As the two stopped near Lung, he turned to go.



Apparently he was going solo.  He clawed at his already scale-torn shirt and cast it aside, then stalked into the crowd.  He didn't \emph{completely} blend in, with his heavy jeans, but he could almost pass for a case fifty-three.



The dense man with the knife stopped.  He'd found a place in a cell where nobody had a good view of him.



He held up the knife, then activated it.   I drew the bugs from beneath his clothes and wrapped threads around the handle.



The lights went out.



I carried the knife up to the ceiling, then started carrying it down the length of the hallway.  With my bugs, I could trace the hallways on either side, sense the general grid with cells in rows of five, I could see the people\ldots



Up until I ran into Mantellum's blind spot.



A chronic failing of human beings, that we so rarely looked \emph{up}.  The swarm moved along the ceiling.  If any parahumans had the powers to notice it, they didn't have a strong enough voice to alert any others.



And, in the interest of using the enemy's tools against them, I was able to bring the swarm inside Mantellum's area of effect.  If there were clairvoyants or precogs capable of tracking my actions or what I was about to do, then this would presumably limit their sight just as well as it limited mine.



They'd lynched one of their own kind, were eager to lynch any others who didn't show absolute loyalty.  They were celebrating, in a way, and they were simultaneously building up the crowd, ensuring that their mob was loyal.  All of them on the same page, for better or for worse.  I couldn't see, but I could guess that the reason for their slow progress was the press of the crowd between them and the door.



I was blind, here, but I didn't have to strike aimlessly.



I extended silk thread above the blind spot.  A good two hundred feet of the stuff, level with the ground.  I only stopped when either end of the suspended silk cord I had bugs on either side of Mantellum's blind spot.



Then I extended more, setting it cross-wise against the other thread.



Not perfect, but it gave me a starting point.  Assuming the blind spot was a circle or a sphere, which it appeared to be, I could find the center point.



Mantellum, the source of the effect, dead center.



I waited until the lights flickered again.  The moment my bugs couldn't see the lights, the tight swarm of bugs with the threads and the dagger swept down.



``Shadow Stalker, Lung, this is my signal.  \emph{Act}.  Imp?  Get out of the way, head back to us.''



One pass.  A lazy swoop with the swarm, the knife suspended by threads.



I couldn't see, even with the camera, but I was aware of Mantellum stopping in his tracks.  The boundaries of the circle stopped drifting in the general direction of the stairwell.



I waited, \emph{willed} the lights to flicker.  Time passed.



People were reacting, outside the circle.  How much damage had I done?



The lights went out.



Another pass.



Mantellum's effect dissipated.  The blind spot filled in, a crowd, capes, blood spraying.  My bugs could sense them all.



The lights came back on.  One cape saw the swarm, moving towards the ceiling.



A chunk of ice the size of a small car hit them.  Ice fragments rained down on the crowd.



Many bugs had died in the collision.



The swarm couldn't keep the knife aloft.  I had to reinforce it, but I couldn't get enough bugs there in time to do it before it hit the ground.



Fine.



I let it fall.  Let it pass through the ground like the ground wasn't even there, disappearing into the floor beneath us.



``Custodian,'' I said.  ``The effect that was blocking you is down.''



I could feel her move.



Lung was advancing, now.  Fire rolled forth from his claws in plumes, surging into cells.  The crowd moved out of his way.



I could hear them cheering.  Oblivious to the fact that he wasn't on their side, wasn't just carrying out the raid.



Lung hurled a fireball that passed just \emph{inches} above the crowd's heads.



The fireball hit a cell block, scattering more of the crowd.



He was changing now, changing quickly.



``Lung,'' I said.  ``Tone it down.  If you grow too much, you won't be able to come downstairs.''



No response.



More fire, more destruction.  The flames were spreading, igniting beds.  I could see on the camera, the meager flames that lingered on stone and concrete.



There was a method to his madness.  Small as the flames were, capes were backing away a touch.  They were cheering him on in his rampage, cheering the destruction of cells that had kept them captive, but they were still falling victim to the strategy beneath it all.



He was walling them off, sectioning off an area with fire and plumes of smoke.  Making it so we only had to deal with a smaller number.



I became aware of Imp as she hopped over a smaller flame on her way to us.  Lung, unaware due to her power or uncaring due to his personality, came dangerously close to frying her as he shored up the barrier, driving people back as the smoke continued to billow.



The cheers became screams of fear and panic as Shadow Stalker's bolts started hitting the special capes.  Sniping them.



Three shots, and then someone retaliated.  A sonic attack, focused.  The crossbow bolts stopped appearing.



\emph{She's dead?  Just like that}?



No.  More crossbow bolts, from a different vantage point.  Fired from within walls, Shadow Stalker poking a barely visible head out into gloom to get a bead, then firing at her targets.



``Go,'' I said.  ``Shadow Stalker, Lung, we're moving.  Cover our retreat, follow us if you can.''



No response from either.  They were busy doing what they were doing.



I could feel the Custodians appearing.



A vast quantity.  Filling empty spaces, overlapping.



\emph{A duplicator?}  I thought.



Like Velocity, the Brockton Bay Protectorate member who'd died against Leviathan.  He'd been a fast cape, capable of outrunning vehicles, striking a hundred times in a minute.  But that came at the expense of a limited ability to affect the world.



The Custodian was the same.



She was weak, standalone, barely a wisp of air.  And she couldn't turn it off.  Couldn't get back to a state where she was fully material, capable of affecting the world normally.



But she duplicated, combined her strength, made hundreds of herself, \emph{thousands}\ldots



She tore into the crowd like an elemental force.  My bugs could feel the air ripple, felt prisoners get thrown into cells.



Felt the blood, the limbs being bent in ways that wasn't possible, when they refused to be thrown.



Energy attacks cut through the open air, and she barely slowed down.



The remaining \emph{special} case fifty-threes from the floor below started to attack, to use abilities I couldn't quantify as sound or fire or lightning, and the Custodian let hundreds of duplicates disappear in her attempts to get out of the way.



We headed out of the corridor.  ``You two,'' I ordered the shirtless duo.  ``Help defend us.''



Between the dogs, Golem and Cuff, we had the brawn to force ourselves through the crowd that was in the area Lung had walled off.  Surprise, too, went a long way.  I didn't have a lot of bugs, but I had enough to blind a few people, to fill their noses and ears and distract.



When Lung turned his fire on the group that was standing their ground, readying to stop us, that was a breaking point.  They scattered.  Two remained, tough and stubborn enough to keep attacking, and Lung picked one of them up, swinging them like a flail to bludgeon the other aside.



Golem's hands shoved more away.  Cuff's strikes, using her ability to manipulate metal and her metal gloves, were enough to break bone.  She shattered legs and arms, struck ribs and threw people aside.



I wasn't \emph{proud}, but I knew that this cold, efficient ruthlessness was at least partially a result of the time we'd spent together.



Imp caught up with us.  She had a sphere tucked under one arm, with the coiling mass of Weld's partner within, still moving.



Panting, Imp said, ``Couldn't get him, but I figured she's bound to be on our side, right?''



I only nodded.  There were other things to focus on, like the ones that had been torturing her.



In the stairwell at the far end of the hallway, the one that mirrored our escape route, the main group, with the beautiful man, the spiky boy and a badly injured Gully were making their way down the stairs.



I was ready.  I already had thread attached to a rivet in the ceiling, thread attached to the knife I'd dropped to the floor below.  It swung into the stairwell, an easy, casual swing.



The disintegration effect carved into the people at the front of the group, into heads, shoulders, necks, and body parts unique to case fifty-threes.



I used the swarm to control the swing, to swing it \emph{into} the crowd that was hurrying down the stairs.



More struck.  Devastation, people falling over each other as they collapsed on the stairs.



Someone, no doubt someone with a sensory power, reached for the knife, tried to grab it.



I cut the thread with the mandibles of my bugs.  It plunged down into the group, paused as the handle came to rest on writhing bodies.



Then slid off to one side as the blade continued to eat through everything near it.



Again, it ate through the stairs, falling to a floor below.  I did what I could to catch it, using my bugs to grab after the threads that still trailed behind it.



We reached the stairwell, and faced the group within.



They'd barely dented the reinforced metal doors, with their myriad powers.



Cuff ignored them, charging forward, and hit the door with her fist.



The crash was loud enough to stun \emph{me}, and I was at the thick of the group, furthest from the door.



She did more damage to the door than most of them had.



\emph{The Custodian was right.  We wouldn't have been able to break through here in normal circumstances.  We'd have been cornered, more than we were in the cell}.



The damage continued outside.  The Custodian pursued the group in the stairwell, harassing, bludgeoning.  She separated the crowd into groups and then bulled them back, driving them towards empty cells.  I was drawing my bugs back to me in stages, concentrating them on a few people at a time, trying to track what she was doing.



Yet even with that, I couldn't follow it all.  Flayed skin, people holding their hands against one eye, joints bent the wrong way, bleeding wounds.



Nothing lethal.  Only punishment.



Lung, Cuff, Golem and Rachel dealt with the five threats here in the stairwell.  Shadow Stalker made her appearance, and dealt with the sixth, jamming a tranquilizer bolt into his neck.



Cuff hit the reinforced metal door again.  It bulged as if she were ten times the size, hitting ten times as hard.



She hit it a third time, a fourth\ldots



On the fifth impact, it gave way.



We made our way down.



``Further,'' I said.



``\emph{FYI,}'' Tattletale's voice sounded, ``\emph{Losing y}ou as you get further down\emph{.''}



``We'll be in touch,'' I said.



``\emph{Attack in Gimel went.  Not good, not bad, but it went.  Didn't want to dis\ldots, but now it's\ldots    \ldotsJust wanted to let you know.  Bracing ours\ldots \ldotsr nex\ldots he didn't show at next location\ldots trying\ldots  where he is\ldots Wish us-``}



And then radio silence.



I tested the comm.  No luck.



Two stairwells, mirroring, no doubt for the safety of having a backup.  The other group had stalled where the knife had delayed them.  We proceeded further.



Past the fourth floor.



We stopped, panting for breath.



Another reinforced door, open.



An expanse of flat, brushed steel behind it.  A dead end.



And sitting in front of that expanse of steel were Satyrical, Blowout, Floret and Leonid.  Revel and Exalt were nowhere to be seen.



``It seems we're going to have ourselves a problem,'' Satyrical said, looking down at his fingernails.



``No offense,'' I said, ``But I think we're a little stronger, in terms of raw firepower.''



``You are.''



``So unless you've replaced half of my team with sleeper agents\ldots''



He shook his head.  ``Only just became aware of you, honestly.''



``\ldotsI'm not particularly threatened.''



``No,'' Satyr said, speaking slowly, as if he were picking his words.  ``It's not us.  It's him.''



Him?



Oh.  Him.



``And the one with the answers is buried under a half-mile of solid steel,'' he said.  He bit at the corner of one fingernail, then buffed it on the leg of his costume.  ``Like I said.  A problem.''





