





``Weaver,'' Cuff said.  Her voice was pitched low enough that Satyr wouldn't hear.



I turned my head her way to acknowledge her.  Satyr seemed to be preoccupied, sitting on a stair, picking something out of a groove in his golden belt.  Dried blood?



``You're doing that crazy mastermind thing again,'' Cuff said.



``Which crazy mastermind thing?''



``Where you talk to the \emph{other} masterminds and one of you leaves something unsaid, and the other \emph{knows} what that thing is without asking.  \emph{Who's} here?''



``Scion,'' Satyr said.



``You heard me?'' Cuff asked.  Then, after a pause, she asked, ``\emph{Scion}?''



I spoke up, ``Leonid's powerset includes the ability to hear everything in a certain range.  That means everything, regardless of intervening obstacles, interfering or distracting noises and volume.''



``I can hear your heartbeats,'' Leonid said.  He was a lean, young twenty-something with long golden hair and a mask with a lion motif.  His upper body was draped in a black, skintight, sleeveless, bodysuit, his legs in loose-fitting pants.  Complex looking gauntlets and boots encased his extremities, each tipped with wicked, six-inch claws.  Not quite what he'd worn when he was on the Vegas Protectorate team.  His eyes roved from Cuff to Imp.  ``I can hear your heartbeat speed up when you look at particular people.''



``Satyr can tell you he already tried the seduction angle with his copies,'' I said.



Leonid grinned behind his mask.  ``Satyr was doing it to distract you.  I'm not like that.  I'm one of the active guys.  It's like how a magician shows one hand, all action, style and flourish, to get your attention\ldots''



He gestured towards Satyr, ``\ldotsand the other hand is busy with the trick.  Hate to break it to you, but I'm genuine when I make a move.''



``Yet you're all man-whores at the end of the day,'' Imp said.



``Imp,'' I spoke, my tone a warning.



Leonid only smirked in reply.  Floret, for her part, cleared her throat.



``You're from Vegas, right?  Just because you \emph{dress} like a woman doesn't mean-''



``Satyr,'' I said, cutting her off.  ``You think Scion's here.  Is he down there with the \emph{Doctor}?''



``He entered through the same gateway we did,'' Satyr said.  ``I imagine he's somewhere upstairs.  It was always one of Cauldron's greatest concerns, that Scion would make his way here through one of their doorways.''



``Why?''



``Cauldron's plan B, their plan C, even plans D, E, and F, if things had gone without a hitch, they would have been deployed from this facility.  Perhaps there is one in a million chance one of the plans potentially \emph{works}.  If they don't, then perhaps they buy the rest of us some time, and a third party figures out a solution.  Or perhaps they get close, and Cauldron uses the time that remains to refine the approach and the idea.''



``The prisoners, all of the people upstairs\ldots'' Cuff said, trailing off.



``Plan B.  Also plan D, if you count the more unnatural deviants,'' Satyr said.  ``Except Scion is now \emph{here}, and he's here \emph{now}.  All of the plans will be forced into effect at once, rendered into little more than alphabet soup.  To top it off, the architect of those plans is out of reach.''



I looked at the solid metal wall.  ``Cuff?''



Cuff focused on the metal barrier.  ``I can tell from here.  It's a \emph{lot} of metal.  I don't know how they did it.  It's all one solid piece.''



``They did it with powers,'' Satyr said.  ``A column, with the panic room dead center.  When they retreated inside, they pulled the switch, and the entire substructure dropped two thousand, five hundred feet below ground, putting the upper end of the column between us and them.''



Floret shrugged.  ``We could handle a computer, a lock, even a vault, no sweat.  But not this.  The plan was to wait for the group on the other side of the facility to forge their way through the steel, or \emph{around} the steel, but someone gave the Custodian a tinker-made super death knife, and well\ldots''



``That was me,'' I said.  ``Nothing to do with the Custodian.''



``Ah, well,'' Satyr said.  ``Good and bad to any situation.  We'll be able to assert control over that group more easily, with their leadership dead.  And there won't be as great a chance that they take the good Doctor out before we can get a word in\ldots but progress will be slower, and we don't have much time to spare.''



It was a relief, on one level, that he didn't seem interested in making a fuss over it.  He'd set Spur and Nix in the way, to keep people from interfering with his group's infiltration, but he seemed fully capable of accepting that there was a snarl in his plan.



I knew it was hypocritical, but a part of me was \emph{bothered} by that.  I didn't want him to be able to take this in stride.  I didn't want a lack of communication, conflicting plans and inter-group issues to be the norm, when the stakes were this high.  Satyr was the type that thrived because he anticipated such.



Maybe I was too.



Satyr looked at the wall to his left.  ``The remaining members of the Irregulars and their digging party have just arrived at the far end of this column.  If we go up one floor, we can cross to the other staircase and make our way down to pay them a visit.  Given that the group watching their rear is\ldots \emph{compromised}, I don't think we'll have any problems taking control of that situation.''



``If we leave now and walk briskly, we'll arrive in eight minutes,'' Floret said.



``My details person,'' Satyr said, ``Would you believe?''



My tone was dry as I replied, ``Somehow, I'm not surprised.''



Details would be Floret's thing.  She didn't \emph{look} it, with bright pink hair, green roots, and a costume of metal `leaves' that left little to the imagination.  Her costume philosophy was the antithesis of my own.  But Floret wasn't a fighter, even less than I was.  She could take a minute or two to create a `bud'.  The bud would then unfold into a complex crystalline shape after a set time, or upon impact with a surface.  They were limited in terms of their size, no more than a foot across, but they were rich in potential, with crude applications on the molecular scale.  Typically stylized to look like flowers, the crystals could bond to surfaces, set touched things on fire, cancel out chemical reactions or just fuck with tinker devices.



As a teenager, she'd had a career as a roving lockpick for villain heist teams, creating keys and fake keycards with cloned magnetic strips, to varying degrees of failure.  It was only when she joined the Vegas team that she found others with the degree of forethought, planning and teamwork that could let her power truly shine.



Her power only worked because of her secondary power, and her secondary power was the big reason she fit in so well with the Vegas team.  An enhanced awareness and processing ability regarding fine \emph{detail}.  She picked up on the little things.  All of the little things.



Satyr leaned back, then rolled forwards, getting to his feet without using his hands.  ``I assume you're coming.''



``Yes,'' I said.  \emph{If only to make sure you don't pull something}.  ``More bodies against Scion.''



``Bodies don't matter,'' Satyr said, as he led the way.  ``One, ten, a thousand, it doesn't make a big difference.''



\emph{Speaking of bodies\ldots  Where the hell is Scion?  }There wasn't even any noise.



Was Satyr fibbing?



No.  It didn't jibe.  Not with the aura of defeat, not with the circumstance, with what Tattletale had said\ldots they were good at the con, but not \emph{that} good.



I changed subjects.  ``Can I ask where the heroes are?  Revel, Exalt and Vantage?''



``With Nix and Spur,'' Satyr said.  ``Most likely disguised as a rock or a bulge in the cave wall.  Blowout hit them with a full-on stunning presence.  They should still be out.''



``I see,'' I said, trying not to reveal how surprised I was.  We'd walked right by the captive heroes.  That wasn't the big issue.  Blowout was.  He wasn't as stylish or attractive as the others, with a featureless mask that had a single `eye' at the brow, his head shaved.  His armor panels had lights that slowly rotated from one color to another, like a chintzy car stereo.  Unassuming, when he wasn't engaged in a fight.  When he \emph{was}, the lights would be flaring, muscles would be standing out, and there would be noise, shock and awe involved.



Blowout wasn't a tinker; he had telekinetically assisted strength, which meant that when he was hoisting a car over his head, he was doing it with his mind more than with his arms.  The strength and durability increased with the size of the audience and the reaction he got from them.  His secondary power was the effect he had on his enemies, feeding on the same reactions that fueled his strength to new heights and leaving his targets stunned, reacting slower, taking longer to pick themselves up off the ground.  On paper, he was the case-in-point of what Leonid had been talking about, the hand that distracts while the other hand sets up the trick.



But, as Floret suggested, it was something of a \emph{thing} for Vegas capes to have `secondary' powers that were actually the \emph{real} power, in practice. Or maybe it was that Satyr tended to encourage a focus in the secondary powers, or a development of those same abilities.  There was nothing on record about a long-term use of Blowout's power, like Satyr had described.  It would be a card he'd kept up his sleeve when he wasn't doing something behind the scenes with the Vegas capes.



I was put in mind of a few of the records and events that hadn't quite fit.  They'd checked, retroactively, for drugs, and found none.  They'd checked for any remainder of Floret's creations, and again, they'd found nothing.  But if it was Blowout\ldots if \emph{he} was the reason people had been left with amnesia, brain damage and even brain death, then that gave me a bunch of new reasons to worry about the Protectorate heroes we'd left behind.



A reason to watch our backs.  I just had to wrap my head around how he might have done this so discreetly, when his power required the obvious and blatant.



Satyr's duplicates, maybe?  Did the copies count as a crowd?



Something to keep in mind\ldots and I had to inform my teammates without Leonid knowing.



I glanced at the leader of the Vegas mercenaries, noting how quiet he was as he ascended the stairs.  He didn't seem worried about anything.  Not us, not Scion, not the riot above.  Was \emph{I} like that, when I was in the zone?  Almost wanting to push him outside of his comfort zone, I said, ``I expected you to ask about your teammates.''



``Spur and Nix?  They're capable enough.  If you've done something horrific to them, then informing me won't help us in the here and now.  I'll have my revenge at a later date, all the same.''



``Fair,'' I said.  \emph{No effect}.



I let Satyr maintain the lead of the group and determine our pace as we moved forward.  He had eyes on the other group with his duplicates, and he had Floret passing information to him with the subtle sign language the group had adopted.  It worked; if we arrived too early, we'd be interrupting the Irregulars before they were through the steel barrier.  If we arrived late, we'd be running the risk that the Doctor would be killed.



For now, I was happy to let them manage that aspect of the plan, while I focused on keeping an eye out for the inevitable stab in the back.  It just didn't \emph{flow}, their attitude now, compared to how they'd tried to cover their tracks earlier.  I knew who they were and I'd seen the records detailing whole strings of crimes, and I wasn't willing to believe they were playing ball with us.



So I watched them, and Floret watched me, because her power was perfectly suited to following what my swarm was doing from moment to moment.



``I don't like him,'' Rachel murmured in my ear.



Imp leaned in to join the conversation, adding, ``You \emph{do} know that Leonid can hear everything that's said in a certain area around him?  There's no point in whispering.'' as if she hadn't just found that out for herself.



``I don't like him,'' Rachel said, full volume.



``That's not what I meant,'' Imp said, a little off-guard.



``He's arrogant, he talks too much, and he acts like Tattletale does when she's trying to pretend she's not in a really bad mood,'' Rachel said.



``It's a rare thing,'' Satyr said, ``for someone to leave me speechless.  I \emph{can} tell you that virtually everyone comes to like me when they get to know me.''



``Everyone likes the manipulative assholes after they've had a chance to do their manipulating,'' Rachel said.



``I couldn't extend that to Weaver, there, and suggest the same applies to her?''



``You could try,'' Rachel said, ``But then I'd have my dogs attack you.''



``Alright,'' I said, stepping in.  ``No more of that.''



Rachel glowered at me.



``He's a weasel,'' Lung growled.  ``I have allied with a man who talked like he does, but it was a man of \emph{substance}.  Not \emph{sex} and\ldots''



``Subtlety?'' Imp offered.  ``Scandal?  Style?  \emph{Sophistry?}''



\emph{Where is she learning these words?}



Lung only glowered at Imp.



``As substanceless a person as he might be,'' I said, ``Scion's upstairs, and we have overlapping goals, so we're allies, or as close to being allies as we're going to get.  No fighting.''



Rachel relaxed as though she'd flipped a mental switch.  She snapped her fingers twice, getting her dog's attention, and then made a gesture without moving her hand from her side, her palm facing the ground.



The dogs eased up just like she had.



I glanced at Satyr, who shrugged.  His tone was light as he said, ``My ego's taking a bruising today, it seems.''



I could see the lines of his shoulders and chest, with him not wearing any armor on the upper body.  Was he maybe just a \emph{bi}\emph{t} less relaxed than Rachel at this point?



Maybe he wasn't at ease around someone who blithely barreled past any attempts at manipulation with unbridled aggression.  A point for us, maybe.



We'd reached the fourth floor.  I stood by, watching for trouble from above, while the others filed through.  I could see how Canary was ill-at-ease, while Shadow Stalker was impossible to read in her ghostly state, passing through the wall by the door.  Cuff and Lung were both rigid, as if anticipating fights, but were confident enough to walk ahead of the rest.  Golem, Rachel, and Imp seemed more in their element, hanging back while the Vegas capes passed through.



``You know what you're doing?'' Golem murmured, as he hung back with me.



I nodded.  ``Mostly.  Just watch your back.''



``For Scion?''



``For \emph{them},'' I said.  ``And yes, I know Leonid hears me.  I know \emph{Satyr} and the others are getting the cliff notes from Leonid.  But they've got secondary goals here, and it's worth watching out in case they try something.  Even if they know we know they're trying something.''



There were nods all around.



Four copies of the Custodian appeared before us as we made our way into the fourth floor.  Each moved slightly out of sync with the others as they moved their heads.  It was only when the third and fourth moved that I realized just \emph{how} they were moving their heads – raising their chins to look \emph{up}.



``I know, my dear,'' Satyr said.  ``How close?''



They didn't respond.  Instead, they disappeared.  First one pair, then the remaining pair.



``Second floor basement,'' Satyr said.  ``Scion is taking his time making his way down.''



``Why?'' I asked.  It was too quiet.  ``If Scion wanted, he could have torn his way through here in a heartbeat.''



Satyr was on point as we made our way across the fourth floor.  The cells here were reinforced several times over, each standalone, separated by tracts of empty space that eighteen wheeler trucks could have turned around in.  Spotlights served as the only light in the area, and they were focused on the individual cells, leaving the empty space between the cells dark.  Without my relay bugs, my power still didn't quite reach the far end.  A third of a mile across by a third of a mile across, maybe, with ceilings that were fifteen feet high.



The lights flickered more violently than it had upstairs or in the stairwells, but \emph{these} cells seemed to be drawing on a backup power source.  The lights flickered, went out, only to be turned back on, glowing a dim red, before the regular power was restored.  The lighting cycled between the three states, with no rhyme or reason.



``\emph{Why}?'' Satyr echoed my question.  I turned my attention back to him.  ``Why do you think he's taking his time?''



``That's \emph{not} helpful,'' I said.



``Basic reasoning,'' Satyr said.  ``What do we have in abundance, here?''



``Capes?'' Golem asked.



``Capes?  Yes.  But there were capes at the other battlefields.  It's very possible he's idling because he's taking them all to pieces, but\ldots for however many minutes?  No.  What \emph{else} is in abundance?  Or, to phrase it better, what particular \emph{kind} of cape is in abundance here, that you didn't have at the battlefield?''



``I get the feeling you already know the answer,'' I said.



He nodded, the goat-horned helm dipping low, then rising.  The lights went out, then went red for a moment.



``Case fifty-threes,'' Golem answered the question.



``\emph{There} we go,'' Satyr said.  ``And if you care to, you can infer further.  \emph{Why}?  Scion is the supposed source of powers, yes?  Then what are the deviants to \emph{him}?  If we see them as distorted \emph{people}, then he sees them as\ldots''



``Distorted powers?''  Cuff answered.  ``Or\ldots whatever they are to him.  Distorted spawn?''



``Something foul,'' Shadow Stalker spoke for the first time since we'd split up to escape the cell.  ``Broken, wrong, loathsome.  \emph{Damaged}.  And no parent wants to face the fact that their kids came out less than perfect.''



The sphere Imp had tucked under one shoulder jerked a little.



``Woah,'' Cuff said.  ``Generalizations much?''



``Tell me I'm wrong,'' Shadow Stalker said.  She glanced at Satyr, ``I'm right.  Cauldron created these \emph{deviants }as a kind of psychological warfare.''



``Most definitely part of it,'' Satyr said, and there was an approving note in his voice.  ``It's psychological warfare\ldots Shadow Stalker, was it?''



Shadow Stalker nodded.



``Yes, I've heard of you.  There are other elements at play.  Prey species have been known to spread their scent through an area, to confuse predators.''



``I like that analogy,'' Shadow Stalker said.



``Mm hmm,'' he responded, nonchalant.  ``So Cauldron uses these deviants as a particularly strong source of our metaphorical `smell'.  They scatter them across the world where Cauldron is most active, the world Scion occupies, and he loses the ability to sniff them out.  Of course, this only works when the deviant isn't going to draw undue attention.  Either they're calm and inclined to keep to their own, by nature, or so dangerous that they remove witnesses by default.''



My eyes moved to the sphere Imp carried.  I was \emph{inclined} to think she fit in the latter category.



``It makes sense,'' I said.  My eyes were on Shadow Stalker.  She was playing into Satyr's hands.  I'd made a note to watch out for it, but this wasn't even \emph{subtle}.



They were fucking \emph{blatant} about this shit, relentless.  Which probably worked for them, because it eventually worked.  They found a hook, an angle, maybe played it in a more subtle way, or they'd just take it and run with it.



And it was all controlled, all \emph{managed}, keeping it at a level where I couldn't call them out on it without looking like I wasn't willing to play ball.  That was fine on its own, but it put us on a bad footing.  I didn't want to be in the middle of a brawl if and when Scion made a sudden appearance.



``Cauldron capes have, according to reports, gotten responses from Scion.  A pause, a momentary break in pattern, even, some say, a \emph{feeling} of aversion.  Powerful Cauldron capes achieve better results, deviants even more so\ldots and if the effect scales up as Cauldron thinks it might, the \emph{extreme }deviants will get an even greater result, while having powers that may have some effect on him.''



``Which makes a lot of sense,'' I said, ``They're a smokescreen, maybe.  Except there's a hole in that theory.''



``There is,'' Satyr said.



``He could wipe them out with one shot,'' Golem said, the first to connect the dots.  ``He could shoot them and shoot through the floor, if he wanted to.''



``Exactly right,'' Satyr said.



``Do you know why he isn't?'' I asked.



``I have guesses, nothing more,'' Satyr said.  ``Hm.  They just found a way of combining their powers.  They're breaking through the column more quickly than I thought they would.  We don't have to run, but maybe \emph{hurry} a bit.''



We stepped up our pace.



``He's on the third floor,'' Satyr said.  ``Floor above us.''



``How do you know?'' Shadow Stalker asked.



``Custodian.  We've crossed paths, as my group ran some errands for the good Doctor.  I think she \emph{likes} me, even.''



I hadn't noticed the Custodian, but I wasn't positive I would have seen her if the appearance was brief enough.



``What's on the third floor?'' Floret asked.  ``I haven't been down here.''



``The ones with names.  Any cape they deemed interesting enough to keep and research.  Not many left.  I think they scaled down on those to focus on other things.''



\emph{Not many left}.  Meaning there wasn't much standing in the way between us and Scion.



\emph{If} Satyr's group wasn't playing us.  I was less sure than I had been.



Supposedly Scion above.  \emph{Who's below}?



``Who's with the Doctor?'' I asked.



``\emph{Ask }her\emph{,'' }he said, pointing at Imp.



I glanced at Imp, who shrugged.



``In the sphere,'' Satyr said.



``There's a button on the bottom.  If you depress it, you can rotate hemispheres.  \emph{Counter-clockwise}, please.  Clockwise opens it, and I'd rather not die.''



Imp looked my way.



``Go for it,'' I said.



Imp turned the sphere.



``Finally.  Fresh air,'' the girl inside said.  She had a quiet voice.  More the type of voice I'd connect to a shy librarian at a party or a sheltered preacher's daughter in the company of boys.



``Sveta?'' I asked.  ``We met on the oil rig.''



``She also goes by Garotte,'' Satyr said.  ``The only reason the PRT didn't put her down was because she's rather hard to kill.  She has quite the impressive body count.''



``Don't say that.''



``She was part of the original invading party,'' Satyr went on, ignoring her.  ``They attacked the Doctor, setting this whole mess in motion.''



``I could hear everything you guys were saying,'' the girl said.  It was only when she said the longer word `\emph{everything'} that I noticed the rasp to her voice.  It would be part of the reason for her being quiet.



``Who's with the Doctor?'' I asked.  The other stairwell was in view.



``When things went bad, it was Weld, me, Brickhaus, Gentle Giant and six others who turned around and protected her.  I wasn't very useful\ldots''



She trailed off.  A second passed.



``Need a bit more information,'' Satyr said.



``I'm \emph{hurt},'' she said, and there was a plaintive note in her voice.  She sounded more like a Canary than a Shadow Stalker.  Not quite the voice of a killer.



``Suck it up,'' Satyr said.  ``Scion's coming, and we need to know what we're walking into.''



``Brick took the guy Blesk brained against the wall, um.  It was the clairvoyant, the doormaker, hurt, the Doctor.  Brickhaus, Magnaat, Munstro, they made it inside.  The others got shot down in the stairwell.  Um.  There was a guy with glasses, and five teenagers who looked a lot like him, only without glasses.  Ordinary looking, pretty much.  Alexandria\ldots''



``Hm,'' Satyr made a noise.  He looked up.



In that same moment, the lights flickered out for the umpteenth time.



The emergency lights didn't come on.



I could sense my teammates, Shadow Stalker, Canary and Lung closing ranks.



``Weaver?''  Satyr asked.



He split in two.  A slow, oozing process, a lump swelling, pulling free, then forming features.  The arms and legs were quick enough, and the details followed, but the new him had no helmet, but slowly reshaped his exterior to match the original Satyr's costume.



``If you keep doing that, I'm going to have to attack,'' I said.



``What's he doing?''  Canary asked.  There was a note of panic in her voice\emph{.}



``Splitting up,'' I said.  I \emph{willed} Canary to pull it together.  Satyr bulged, clearly preparing to make another double.  I called out, ``Satyr, I might need to rephrase.  If you finish making that copy, I'm going to attack you.''



``He can't stop once he's started,'' Floret said.  ``It's a drawback.''



``I don't buy that at all,'' I said.  ``So either you need to be more convincing, or I'm wrong, and Satyr has to learn how to cancel a copy in progress in the next five seconds.''



The bulge stopped growing more parts.  It began retreating into Satyr.



``We need to talk, Weaver,'' Satyr said, still distorted, withdrawing the mass into himself.



Imp spoke up, ``Why is it always \emph{Weaver }you need to talk to?  Never, we need to talk, Rachel.''



``Shut up, you \emph{idiot},'' Satyr snarled the words.  ``There's no time for foolishness.''



``\emph{Idiot?  Foolishness?''}



``What is it, Satyr?''  I asked.



``I've got to ask about your goals.''



``Ah,'' I said.  ``Nothing complicated.  Saving the doctor, getting answers, stopping Scion.''



I found my knife, beneath the staircase, suspended by threads I'd tied to the surrounding area.  I set my swarm to retrieving it.  We couldn't see, but Floret shouldn't be able to either.



``I always had a hard time trusting anyone who doesn't have ulterior motives,'' Satyr said.  ``And now, here, I \emph{dearly} wish you had some.''



``Sorry,'' I said.  ``If you haven't noticed, a lot of us are pretty blunt here, straightforward.  Our goals are what they appear to be.  I really wish you could trust us.''



``And I wish I couldn't,'' he said.  ``Funny how that works.''



I sensed Blowout pacing a bit to our left.  Floret had her hand cupped, like she was ready to throw one of her things.  I gathered the swarm, sensed her tilt her head a fraction.



\emph{Listening}?



How much noise could thirty bugs make?  Or, rather, how much noise could thirty bugs make in the audible spectrum?



No.  That didn't make sense.  Floret sensed details without even trying.



She was faking me out, no doubt.  Distracting so someone else could pull something.



Leonid was utterly still, no doubt focusing on the various sounds.  On heartbeats and breathing, the creaks of our muscles moving and joints shifting.  \emph{He} was the one to watch.  He'd said it himself.  He was the hand that drew attention so the others could pull their tricks.



Which didn't make him any less threatening.



Secondary powers of sound detection and sound manipulation, adjusting select things to be up to twice as loud or absolutely silent.  It gave him a stranger classification, a thinker classification.



His third power was a \emph{mover} power.



``Don't do this, Satyr.  It's insanity,'' I said.



``Your being here fucks it all up, Weaver.  There's too much danger that you'd agree with us, that we'd have the same objectives, regarding the Doctor.''



There a distant detonation, a rumbling passed through the complex.



``What \emph{are} your motives?'' I asked.  ``Do you want to help her or hurt her?''



``Yes,'' Satyr said.



``That's not an answer.  I thought you said there's no time.''



``There isn't,'' he said.



``Satyr, I don't know what's going on, but you've been playing this game of tricks and subterfuge so long you've all forgotten how to walk a straight line.''



``Oh, I remember,'' he said.  ``\emph{We }remember.''



``So you're just going to stand here, idly threatening us, until Scion attacks?  That can't be right.  You've lost your mind.  Something with your power, messing with your heads\ldots''



``You've got it wrong.  Powers from a bottle, they mess with your body.  Subtle things, but stuff you notice.  Heh, the last straight conversation I had with Pretender, he brought it up, joked\ldots''



``\emph{Time},'' I told him.



``Ah well.  It's you natural triggers who get a little bent in the head, here and there.  Isn't that right, Ms. Lindt?''



My heart dropped out of my chest.  I closed my eyes.



``Yeah,'' Rachel said, her voice quiet.



I clenched my teeth.



``That's right,'' she went on, a little louder.



``Shadow Stalker.  You too, believe it or not.  I've seen your record.  Your attitude, it's not wholly your own.''



``Bull.''



``I've worked with worse.  I could give you direction.''



``Honestly?  With this shit you're pulling now?  You sound fucking \emph{crazy}.''



``Shadow Stalker and I are agreeing on this count,'' I said, ``Trust me when I said that's a bad sign.''



``If we're going to resolve this, it'll have to be soon,'' Satyr said.



``You keep doing that,'' I told him.  ``Telling us how little time we have, then delaying.  Forcing us into a corner?''



Another half-chuckle, wry.



``You're not making any sense, Satyr,'' I said.



He only offered another short laugh.



``You \emph{want} us to fight you.  To stop you.''



``Probably for the best,'' he said.



``No, it's not,'' I said.  ``We need help, we can't be distracted by-''



``Enough of this,'' Lung growled the words.



``No-'' I said, but I was too late.



Flames erupted around his claws.



It cast light on us, on our surroundings.



With the light, Floret could see my knife, off to one side.  I hadn't been planning to use it to attack, but I'd wanted it in hand before we descended.  She slung one bud at it.  Encased it in crystal.  It hit the ground at the base of a cell, by a spotlight.



Leonid screamed, double volume, and it was an eerie, echoing scream that bounced through the area, each echo lower in pitch than the last.



Not that he needed it to reach that far.  Each echo of the scream coincided with a fraction of him fading out of existence.



Simultaneously phasing those parts of him in behind our group.



Canary had started to sing, nervous, but Leonid faded in behind her.  Two seconds to teleport.



Rachel raised her hands to her mouth to whistle.  No sound came out.



I turned, opened my mouth to shout, but Leonid had muted us.



I pointed, instead, but Canary didn't get my meaning.



Rachel couldn't get her dog's attention with snaps or whistles.



Leonid reached out with his claw, up for her throat-



And Rachel tackled him, gripping his wrists.  Canary was entirely unawares, up until one of them kicked her ankle in their struggles.



Shadow Stalker and Lung engaged two of the remaining Vegas capes.  Blowout stepped in the way, protecting Floret.



And through some unseen signal, some practiced maneuver, he knew to duck as she flung buds at the pair.



One unfolded in the air, tagging Shadow Stalker in her shadow state, and she crumpled.



The other hit Lung.  Foot-long tendrils extended from his right pectoral to his right arm, binding to each.



Blowout hit the tethered Lung.  Maybe he wouldn't have been strong enough to affect Lung normally, but the \emph{audacity }of it and our reactions to that went a long way in giving him a little extra kick.



Satyr forced another copy out in record time, as the other charged me.



I set my bugs on it.  On \emph{her}.  My double.  She didn't have my powers.



She was strong.  Tougher.  She closed the distance to me with ease, with a runner's strength.



So I moved the bugs to the original Satyr.  That bare chest, the eyeholes in his helmet\ldots  I attacked Floret, and Leonid, and all of the other capes who had exposed skin.



Golem's hand knocked her aside.  Cuff charged the one Satyr had just created.



Even at this juncture, I knew it wasn't an even fight.  Satyr had outright admitted his team wasn't a match for ours in a brawl.



Canary tentatively stepped on Leonid's right hand.  Rachel's dogs got his legs.  He screamed, and \emph{that} sound wasn't muted.



He began to phase out, reappearing by Satyr.  He climbed to his feet.



We outnumbered them, we had better combat powers.  The outcome wasn't in doubt.



Which made \emph{Imp's} maneuver all the more insane.



She stepped out into the middle of the group and held the sphere high.



Rotated it, then rotated it back.



Sound resumed around us, as Leonid dismissed the silence effect.



``\emph{Don't, don't, don't,}'' a voice was saying.



It was Sveta, inside the ball.



``Everyone stand up,'' Imp said.  ``And if you fuck with me, I'm opening this thing.''



``\emph{Don't, please don't.}''



``\emph{Why?}''  I asked, again, my eyes on Satyr.  The real Satyr.



``I would have been content to wait.  To procrastinate until we ran out of time.  But \emph{you} came.''



``Satyr\ldots''



``It's for love, in the end.  Pettiest of all pursuits.  Arrogance, greed, even revenge\ldots they're nobler, trust me.  I've walked all those roads.  But love?  It twists all the other things.  Makes you misstep, makes you irrational, makes you \emph{impatient}, above all.  We couldn't have gone down there without getting revenge, without falling to our greed and arrogance.  So I was willing to wait.  To sit back and put it off, tell myself we didn't have the firepower, didn't have the numbers we needed to take on the group at the stairwell.  Wait until it was too late.''



``You were willing to die?''  Shadow Stalker asked.  She sounded \emph{offended}.



``Better than being the ones who pull the trigger, dash our last hopes,'' Satyr said.  ``You can put down that sphere, Imp.''



Imp hesitated, then lowered the sphere.  She locked it, with vents open so Sveta could speak.



``I don't understand,'' I said.



``And you probably won't.  If you're lucky.  I've said it all out loud, so the lie isn't worth it, now.  You can go.  We'll stand by.''



``Your fucking head games.  You're going to stab us-''



``Weaver,'' he said, and there was no pretense in his voice.  No joking tone or trace of mockery.  Talking straight.  ``Go.  They're almost through.''



``He is right, Skitter,'' Lung growled the word.  ``I can \emph{hear} him.''



Lung was looking the way we'd come.



Scion, here.  On this floor.  I thought I could see the golden light, but it might have been a spot in my vision from looking at Lung with his burning hands.



\emph{If we go, there won't be any escape routes.  No exits.}



It was as insane as anything Satyr was doing.  Everything rational said to go upstairs, to find our way to the doorway, hope that Scion was still half-blind, still holding back.



But I turned, running for the stairwell with the Case-fifty-threes, away from Scion.



I ran hard enough that I couldn't spare the breath.



I spoke with my swarm.



``\emph{Go upstairs, if you want to go.}''



\emph{Give them a way out}.



I could hear the others behind me, at varying distances.  I could sense Satyr's group with my swarm.  They held their ground as Scion approached.



\emph{I don't understand}.



The others were following.



``\emph{If you come, there's no way out.  This isn't even a hail mary, it's a hope that there's maybe something we can do.  A chance buried in a chance.}''



We came face to face with the group that had been working their way through the steel.  A mole-man, an `extreme deviation' case that seemed to be made up of lasers, with her petrified body parts capping the ends.



And others, dead.  Satyr's clones littered the area, where they'd brutally fought and killed several of the digging capes.  Where they'd died, they'd withered.



With Scion on our heels, we couldn't afford the time to fight.



Lung, Shadow Stalker and Rachel tackled the ones who remained.  A crossbow bolt delivered to the cranium of the laser-girl, dogs attacking the mole-man.  Lung's claws and flames to assist with both.



Without my asking, Cuff jumped into the hole.  Imp followed.



One by one, we passed inside.



Golden light flared in the massive room we'd just left behind.  No rumble, no devastation, nothing of the sort.



But I could guess what had happened.



Even if I didn't \emph{understand} it.



Golem was blocking off the path to us, while others made their way down.  Lung, Canary, then Rachel and her dogs.  Hands of concrete barred the way, and two larger hands extended from the column, fingers knitting together to form a fence.



It wouldn't hold Scion for \emph{seconds}, but it was something.



Three of us remained.  Golem, getting ready to descend, me, watching the rear, and Shadow Stalker.



Our eyes met.



She bolted, disappearing through the wall.



I headed down, with Golem following right behind.





