





It wasn't the most comfortable journey.  I could handle uncomfortable.  Uncomfortable was better than being upstairs and staring down the bastard that was exterminating humanity.



The opening of the tunnel had ridges, bumps and uneven edges that scraped past me with enough speed and force that I worried it would damage my costume.  Probably intentional, giving traction to the ones who weren't digging.  But we passed that area and we hit smoother metal.  Traction was harder to come by, the tunnel almost a winding waterslide.



I slid, as the others were doing, bracing my feet against the sides to slow my descent.  The bugs I'd planted on my teammates let me track the turns and drops, angling and bracing myself as I ran into steeper drops, sharp turns and outright ten foot drops.



It reminded me of an anthill, in a way.  Winding tunnels, irregular, exploratory, treacherous and impossible to navigate.



Cuff slid down and hit the end of the tunnel.  A dead end, with a person there.  She didn't slow, instead using her power to hammer her way through, splitting the steel apart and driving herself and the individual at the end through the resulting hole.



The instant Cuff was through into the room on the other side of the tunnel, she and the individual she'd collided with were attacked.  Lung was the next in line, followed by Canary, and they were ambushed as well.  Lung was pinned against a wall, Canary liberally \emph{tossed} back into a crowd that waited to disable her.



With Golem behind me, I didn't want to stop and get my bearings, but I was plunging towards a situation I couldn't fully grasp.  Bugs I'd planted on my allies spread out, but it was too few to get a good picture of who and what was waiting for us.



I didn't have Defiant's knife.  Floret had encased it in crystal.  I could drag it here, maybe, or use relay bugs and wait for the crystal to expire before carting it my way, but that didn't help me \emph{here}.  I called for my bugs to bring the knife anyways.



Rachel had paused before entry, getting herself sorted out with her pets, meaning she was only just arriving.  Her reactions were fast, the commands to her canines quick and efficient.



They swelled as they put themselves between her and the waiting group, growing in size and manifesting their natural weapons.  It was fast enough I suspected she'd been starting their growth as she approached the literal light at the end of the tunnel.  Bastard's changes were more fluid, faster, and more symmetrical than Huntress', but he was younger, just a little smaller.



A group advanced on the canines without fear.  Two people to Huntress, two to Bastard.  Young men, if my swarm-sense was correct.  The animals weren't as big as they could get, but they were about as large as a couch.  Yet the men didn't show any fear.



They moved fluidly as the animals lunged, snapping and biting.  Confident movements.  Two caught Huntress' head, wrenched it to the side, while the others avoided snapping jaws to catch Bastard's forelimbs, bodily hauling him up and then throwing him to the ground.



The two animals were brought down in as many seconds.  Pinned, as inexplicably as \emph{Lung} was pinned.  Except this wasn't sheer strength.  They were strategic, targeting body parts, one of the young men leveraging his whole body between Bastard's forelimbs, forcing them apart in a way that the dog's musculature couldn't combat.



It was like holding a crocodile's mouth shut.  Jaw strength aside, the crocodile wasn't built to force it's mouth \emph{open}.  The wolf wasn't built to draw its legs together against its chest, but couldn't get feet under it to stand without dislodging the offending attacker.  The other had his head caught and twisted to one side.



Huntress, for her part, was caught by the head alone, which had been forced down.  The woman who had Lung pressed up against the wall had one foot on the dog's muzzle, and was holding it down.



They made it look so easy it was almost \emph{effortless}.  A fifth boy approached Rachel, now disarmed of her dogs.



I forced myself to slow down as we approached a flatter spot.  Theo's heavy metal boots hit my shoulders.



We were still sliding down, but slower.  Only seconds before we were through.



``Ambush below,'' I managed.



No response.  Whoever had dug the tunnel had been digging \emph{down} when they reached the edge of the room.  I supposed they'd stopped when they reached a layer made of a different material, going up to check.  Our entry was a straight drop into one end of the room, and I landed flat on my back, nearly colliding with Rachel.



A boy.  A teenage boy, clean-shaven, if he even needed to shave, wearing a white dress shirt with the sleeves rolled up the forearms, his blond hair slicked back, and black suit pants.  He backed away a step as Golem and I appeared.



His appearance, the way they'd fought\ldots like Contessa?



Each of the boys were identical.



Lung and Huntress were pinned by Alexandria.  Or by Pretender wearing Alexandria's body, in a way.  Lung was changing, the canines swelling in size, and yet she didn't look worried.  Bastard was still on the ground, one of the boys looking as unconcerned as one could look while holding down a half-ton animal.



Behind the boys, a small crowd had gathered.



Doctor Mother, a Manton with the Siberian\ldots or a Manton \emph{clone} with the Siberian, a claw pressed to Gully's throat.  There were three more case fifty threes, all burly, all bound with heads hanging.  Rounding out the group was the Number Man, who had a pen pressed tight against Cuff's jugular, her costume already torn open at the throat to expose flesh.  His foot was propped up on a sphere.



I could see the resemblance between the Number Man and the boys in dress shirts.  Twenty or more years of difference, and the Number Man was dressed in a full suit, which somehow made him more imposing, pocket protector or no, but they were too similar to be anything but related.



Was Cauldron cloning?  Another contingency plan?



At the very back of the room, separate from the group, were two pale young men, laid out on desks that sat on either side of a reinforced door.  A twenty-something guy with flat skin stretched over where his eyes should be, and a guy that was maybe ten years older, with enough bloody bandage around his head and face that I couldn't make out his features.  Doormaker, I could assume, based on what I'd heard upstairs, along with the clairvoyant the Doctor had mentioned in the past.



The boy in the suit closed the distance, and Rachel struck out.  He batted her fist aside.  She kicked, and he casually caught it and leveraged it to throw her off balance, tossing her to the ground.



Maybe a little harder than he had to.



I saw how she fell, saw her back arch, the way she held her arm as she rolled over.  She didn't cry out, didn't make any sounds of pain, but the degree of pain was clear.



\emph{A lot harder than necessary}.  Had she broken something?



He turned his head towards Golem and I, and he smiled a little.  A tight, narrow, mocking smile.



``I'm not your enemy,'' I said.



``You came out fighting,'' Alexandria-Pretender said.  She looked down at Rachel.  ``Or \emph{she} did.''



``Bastard was acting like there was fighting going on, ears, hackles up.  You attacked us.''



The Number-Man clone kicked her.  Casually cruel.



I tensed, but I didn't act.  The fall had knocked the wind out of me.  Catching my breath, then-



``Disable her,'' the Doctor said.



The young man closed in.  Still smiling.  Fuck me, was that smug smile irritating.  I felt a moment's sympathy for people who'd had to face down Tattletale.  I sicced my swarm on him.



He moved through the incoming insects, eyes open and unblinking as he closed the distance to me.  Only a few landed, and they landed in spots where they couldn't target more vulnerable areas.



That he wasn't closing his eyes was telling.  I used my bugs to try and blind him, to keep him from seeing how I was moving, and I reached behind my back, going for the pepper spray.



He blocked my wrist with his palm, keeping me from aiming at him.  Not just sight.  Or his sight was more acute than I'd realized.  Hearing?  Something else?



\emph{Be unpredictable}.



Pepper spray killed bugs.  I didn't aim for him, but for the pair of us, spraying into open air, into my swarm.



I'd hoped to make him back off, but he didn't.  He ducked low, simultaneously bringing one foot \emph{up}, catching me in the chest.  In the same movement, he rolled to one side, getting away from the mist of pepper spray that was still hanging in the air and simultaneously avoiding Golem's reaching hand of concrete.



For just an instant, my feet left the ground.  I landed, but I landed with one foot on Rachel's calf.  I fell.



Too much like fighting Contessa.  Everything winding up positioned \emph{just right}.  Damn it.



On my back, I was vulnerable, but Golem was covering me.  This kid with the dress clothes was slippery, efficient, but the way his movements played out\ldots maybe not quite on Contessa's level.  Contessa would have found a way to attack and defend at the same time, instead of being stuck evading Golem's power.



I tried to haul air into my lungs and coughed instead.  If they killed us before we got far enough\ldots



\emph{Stupid, all of this, so stupid}.



``\emph{Stop,}'' I spoke through my swarm.



The kid drew knives from his pockets.  Small knives, with blades no longer than a finger.



Still confident, still \emph{sure} of his victory.



A connection formed in my head.  I knew, in an instant.  \emph{Harbinger}.



Cauldron had collected some of the remaining clones from Jack's army.



\emph{The Number Man used to be in the Slaughterhouse Nine?}



No, couldn't get distracted.  I was up against a kid with an analysis power that was off the charts, he'd dodge whatever I threw at him.



I used my pepper spray again.  This time, I aimed at the two boys who had Bastard pinned.  Opponents who couldn't dodge, not without giving up an advantage.  They moved out of the way, and in the process they let Bastard climb to his feet.  He was half-again as large as he had been, a ridge of stegosaurus spikes along his spine, more spikes and barbs framing his face.  He growled, and it wasn't a dog sound.  It wasn't a \emph{wolf} sound either.



Bringing two more of the kids into the fight, but now I had Bastard for backup.



Up until Alexandria-Pretender grabbed Huntress and hurled her at us.  Me, Golem, Rachel, and Bastard were slammed into the far wall by Huntress' bulk.



Lung was still growing, still changing, and his throat was broad enough now that she couldn't do more than dig her fingertips into the front of it, but he still couldn't break free of her grasp.



He opted for a second option, leveling a hand at the Doctor, Manton, the Number Man and the crowd of boys.  Fire erupted forth.  A half-second's worth, before Alexandria threw him down and kicked him full-force into the wall beside us.



No use.  The Siberian had saved them with her ability to grant her own invulnerability effect.  \emph{Thankfully.}  If he'd torched them, all of this would have been for nothing.



Had to account for Lung's behavior.  Keep it in mind.  He had a kind of pride, and it had nearly fucked us on two occasions so far.



``We're--'' I started to speak.



But Lung roared, drowning me out as he pulled free of Alexandria's grasp.  Not breaking her grip, but rending his own throat, tearing jugular and vein, windpipe even, in his furious attempt to get free.



Alexandria turned as Lung fell into a fighting stance.  Less a martial artist's stance than an animal, low to the ground, chest heaving to pull air through the gushing wound in his throat, a glare leveled at his opponent.



``Stop!'' Imp called out.



It took me a second to place her.  Behind the Doctor, a knife pressed against the Doctor's throat.  She pulled the Doctor back, away from Siberian.  ``If any of you move, I cut.  This is--''



The Number Man fired something from hip level.  A spark marked the bullet's contact point at the mouth of the hole we'd come through.  The weapon flew from Imp's hand.



``--pointless,'' Imp finished.



The Siberian crossed the distance, then stopped beside the Doctor.  She put a hand on the Doctor's shoulder.



More fighting.  I clenched my fists.  Stupid.



``Scion's here,'' I said, taking advantage of the momentary pause in the fighting.  



Two and a half words to cut through the tension.  I could see the change in the Doctor's demeanor, the Number Man, even the Manton clone.  One of the most powerful groups in the world, in every sense of the word, in raw powers, in political power, influence, knowledge, and they were \emph{spooked}.



I hadn't wanted to \emph{win}, only to buy a chance to talk.  Now this was it, and I had to get them to \emph{listen.}  Simpler was better.  Straight to the point.



``We don't have reason to trust you,'' the Doctor said.  ``We've interacted, Weaver, I have a level of respect for you, but that doesn't extend to equal measures of \emph{trust}.  You're dangerous, and I can't rule out that this is an assassination attempt.''



\emph{Translation: pure denial}.  \emph{You don't want to believe me}.



``He's upstairs and he's coming \emph{now},'' I said.



``That--'' the Doctor started.  She paused, as if reflecting, taking in the implications, then shook her head a little.  ``That doesn't change anything.  I still can't take your word for gospel.''



That sounded less like pure denial and more like outright suspicion.  A step forward, I was pretty sure.



The whole structure rattled.  I felt things sway a touch.



The Doctor looked up, then looked down at me, her gaze level, eyes narrowed slightly.  It was the first time I'd seen her with her hair down, rather than pinned up with chopsticks or some ornate pin.



``I don't know what to say, except that things are pretty fucking dire,'' I said.  ``Satyr's dead, for one thing.''



Alexandria flinched as though I'd slapped her and she had \emph{felt} it.



I looked at her.  ``His team, dead.  The prisoners you guys had on the second, third and fourth floors, all dead or dying as we speak.  Read my expression, use Alexandria's power, tell me I'm wrong.''



When Alexandria replied, the voice wasn't quite Alexandria's.  ``I'm afraid I haven't had the chance to study that in depth to the degree she did.''



``It's fine,'' the Doctor said.  ``I'm willing to believe it, if this is an assassination attempt, I'll take the risk.''



``If it was an assassination attempt,'' Imp said, appearing at the far end of the room, ``I'd have offed you.''



The Doctor glanced her way.  ``And you are?''



Imp sighed.



``We'll make our way downstairs,'' the Doctor decided.  ``William, please rotate the column while our\ldots guests pick themselves up.''



Manton approached a computer terminal set into the wall and began typing.



\emph{Pick ourselves up}.  As if they hadn't just bludgeoned their way through us.



Manton's work at the computer produced results.  The swaying feeling I'd experienced a moment ago hit me again.  Everything I could see was still, but for people trying to catch their balance, but my non-parahuman senses told me we were moving.



It faded.  Rachel ordered her dogs to stand, and the pile of us got ourselves sorted out.  Lung was just at the midway point between human and monster, covered head to toe in overlapping metal scales, his neck a little too long, his shoulders too broad, had a claw pressed to the bleeding throat wound.  By all rights, he should have been dead, but regeneration and an inhuman constitution went a long way.



Huntress got out of the way, and I made my way to my feet.  I could feel the dull pain where bruises would emerge.  If I lived that long.



There was another rumble, and a feeling like I was swaying, my sense of balance not quite right.  Not Manton, so it had to be Scion.  Had the steel column moved a fraction?  Had it been intentional on Scion's part, or a result of the action upstairs?



The Number Man gave Cuff a hand in standing, and she began folding up the metal around her neck, repairing the armor.  She withdrew the wickedly sharp spikes at the knee and the base of her wrist, where she'd been shaping weapons in case she needed to fight her way free of his grip.



He only smiled, tapping one spike with his pen before it slipped into her costume.  Cuff's expression, where her lower face was visible beneath the layered visor she wore, wasn't the slightest bit amused.



The boys with suits tended to the three prisoners and the two wounded.  Alexandria tore off a thick metal table leg and wound it to bind Gully's hands behind her back, before hoisting the unconscious case fifty-three up, carrying her.



``I'm sorry,'' the Number Man said, to Rachel.  ``For the behavior of my clones.  They're inaccurate, based on hearsay and speculation more than fact.  I was more polite, back then, more efficient.''



Rachel just gave him a funny look and shrugged her way past him.



I was tense.  It wasn't just the fight we'd left behind.  Here, we had answers available, but so little time.



I held out my hands.  Floret's crystal with my knife inside dropped from the hole in the ceiling.



The Doctor typed a code into a keypad at the end of the room, and the Siberian opened the door beside it, turning a wheel to unlock it, then pushing the thick metal door open with a disconcerting ease.  Clone or not, she was still the \emph{Siberian} in power.



With the door now open, we were faced with a corridor, wide enough for my group to walk side by side, the Doctor's group leading the way in front of us.  Vials lined the walls around us, set into an arrangement of metal wires that kept them lined up, multiple vials of the same color lined up beside another arrangement of vials.  Except nearly every vial was empty.  There was only glass, no fluid inside.  Where fluid did exist, the light filtered through and cast dark blotches of color on the gray walls behind.



But if I counted them, if I used my bugs to note the ones that had contents\ldots



One or two hundred, maybe, with fluid still inside.



``Our stock,'' the Doctor said.  ``Nearly depleted.  We gave the formulas out for free, in hopes of turning out parahumans that could do damage to Scion.  We retained only the volatile ones.''



``Volatile can be good,'' I said.  My eyes noted the sheer number of vials.  Tens of thousands, even, virtually \emph{covering} the walls on either side of us.



``Volatile can kill three quarters of the people who ingest it,'' the Doctor said.  ``Or generate case fifty-threes we can't use.''



``Right,'' I said.  ``Nevermind, then.''



Each was marked with a combination of letters and numbers, and a title.  I read the names of the ones that still had fluid inside.



Abel.  Abbatoir.  Access.  Ace.  Aegis.  Air.  Alchemy.  Alias.  Alpha.  Amaze\ldots



``So many,'' a voice said.



The ball with Sveta inside.



``Quite a few,'' the Doctor said.



``All tested on people?''  Sveta asked.



``Yes,'' the Doctor said.



``I remember, you know,'' Sveta said.  ``I dream of home.  I was a fisherman's daughter.  There were these beautiful little huts with flat roofs, orange clay brick against gray mountains, with green-blue grass and ocean.  It was cramped, and I had to share space with my family, my siblings\ldots but I was okay with it.  There weren't any boys my age to marry, and I didn't want to move to another town to look for a husband, so I just stayed by myself.  I'd draw, and there was a peace in it.  I \emph{still} like to draw, I find it helps me relax\ldots but it's hard because my tendrils break the brushes and pencils.  And then I don't feel relaxed anymore.''



``We've caused you difficulties,'' the Doctor said, not even looking at Sveta.  She walked quickly, her eyes roving over the rows and columns of vials.



``I can't remember my mother tongue, Doctor.  I can't remember my daddy's face, or my mommy, or either of my brothers.  I've just got the faces I see in dreams.  Every morning I was in the asylum, I would wake up and I scramble to draw something, to put words in a diary, and I'm so excited and panicked and desperate I'd break things.''



The Doctor wasn't reacting.



``I know I used to draw, but I can't \emph{find} the style I used to draw in.  I dream about the night you took me, you know.''



``Not me, surely.  I sent others.''



``You sent people \emph{like me} to take me.  Case fifty-threes.  Branded.  Abominations.  Demons.  There's names for us all over the world.  It was storming, I was delirious, and they came, they grabbed me, and I all I could think was that the old stories were true, and I said something I can't remember.  You took me to a lab and you \emph{unraveled me }with that drug of yours, and then you dropped me in the middle of nowhere, with just enough memories to know that I should be \emph{human.}''



``We gave you a second chance.''



``I didn't \emph{ask} for one.''



``It's very possible your town stood to be destroyed by a storm--''



``If you'd \emph{asked}, I would've wanted to weather it.''



``Or by plague, starvation.  It could be the cause for your delirium.''



``I would've stuck it out.  You're not \emph{listening} to me, Doctor.''  A flare of anger.  The ball bucked with the movement inside.



``There are more immediate problems to focus on,'' the Doctor said.  ``I understand where you're coming from, but this isn't the time to play `what if'.''



``I'm not \emph{playing},'' Sveta said, and the anger was gone, just as fast as it had appeared.  ``I'm- I'm telling you that if you'd asked, at any point along the way, I'd probably have told you I'd rather be dead.  I'd rather be dead than live this new life you gave me, where I spent years killing people by accident, unable to sleep, killing stray animals for food because my \emph{body} decides when I eat, not my mind\ldots''



``I understand,'' the Doctor replied.  She sounded a little impatient.  ``Then damn me.  Curse me.  Tell me I will go to hell for what I did.  At the end of this, I will face any and all punishment that I'm due, alive or dead.  For now, we see our way through this.''



``You don't get to \emph{do} that.  You don't get to get off with\ldots \emph{words }and sentiment.  Gully told me she'd break down in tears \emph{all}\emph{the time, }because moving her arms, being strong enough to break things, it reminded her of what she is, every time she did anything.  Her \emph{power }reminded her, being constantly aware of the ground around her.  Weld\ldots he told me once that he felt like he was going crazy.  All he had was music.  It was the only\emph{ }human thing he could enjoy, because he couldn't taste.  He couldn't \emph{feel}, even when I squeezed him hard enough to dig into him.  And Gentle Giant--''



``Are you going to run down the \emph{entire} list?''  The Doctor asked.  Her voice was a little harder.  ``Do you want an \emph{apology}?  You said you don't want words.  Would a gesture do?  Should I take a scalpel to my face?  Carve myself up so I could experience what you have?''



``It wouldn't even be \emph{a fraction }of what any of us have experienced,'' Sveta bit out the words.  ``Because you'd have had the \emph{choice}, Doctor.  The choice to do that to yourself.  Because we're all going to die when Scion comes down here and you would live \emph{minutes} like that, instead of \emph{years}.''



``Then what do you \emph{want} from me?''  the Doctor asked, and the hardness in her voice had become anger.



The structure rumbled.



The rumble was followed by a heavy crash.  With my bugs, I could tell it was in the room we'd just vacated.  A virtual \emph{waterfall} of debris, of metal slag and concrete.



There was no order, no signal, but we broke into a run.



``I want my \emph{name}, Doctor,'' Sveta said.  She wasn't running, so her voice was level, free of panting or anything of the sort.  ``Not even my old name, from before you wiped my memory.  Tell me the name you gave me, after you sent me to the fourth floor.  Because you do that for the ones you think are worth studying, right?  Or tell me the name I took after you released me into the wild, as some kind of \emph{smokescreen} for Scion.  It starts with `S', if that helps.''



No response.



\emph{We should be strategizing,} I thought.



But I didn't interject.



``You wipe our memories when you send us down to the third floor, Shamrock told us, so I just had a number for a while.  Tell me you remember my \emph{number}, even.  Tell me that what you did to me had \emph{some} merit, that you did all this for some purpose, and turning me into a killer with a triple-digit body count mattered enough for you to \emph{remember}!''



The Doctor huffed out the words, panting as she ran, ``You can't have any successes without failures.  There was nothing of use in your case, nothing memorable but your durability, but it was one formula we could rule out.''



``That's not \emph{good enough}!''



The Number Man spoke, ``He--''



``Not you!'' Sveta hissed.  ``You remember, probably, but--''



``He's here,'' the Number Man said, talking over her.



We stopped, turning.



A golden light at the entrance to the corridor.  A figure stood in the middle of it, darker in contrast to the light surrounding it..



Scion.



He advanced on foot.  One step, then another.



His eyes moved to the vials.



He touched one, gentle, almost inquisitive.



``Oh fuckballs,'' Imp whispered the word.



We backed away, slowly.



Scion reached out and cupped his hands around the vial.  I could see fragments of the wire that held the vial upright falling to the ground, glowing gold where his power had burned through the edges.



He cupped the vial in his hands, staring down at it.



``What \emph{are} they?'' Golem asked.  ``The vials?''



``Powers,'' the Number Man said, unhelpfully.



Scion stared, his eyes roving over the rows of vials.  He reached out for a patch of empty vials, without any color behind them, but he didn't touch them.



Sensing the traces of what they'd once contained, maybe?



Nowhere to go.  Gully might have been able to dig an escape route, but she had a hole in her shoulder I could have put my arm through, and she wasn't conscious, let alone coherent.  Either the impact with Cuff or the fight with the Doctor's people had disabled her.



She'd been with the group that had tried to lynch the Doctor, so maybe taking her out of action had been a preventative measure.



The Doormaker, none of it worked.



``Doctor,'' I said.  ``You don't have powers, right?''



``I don't,'' the Doctor said.  ``But I have a \emph{corona pollentia}.''



``What do you mean?'' I asked.  ``You have the potential for power?''



``I do.  I could theoretically trigger.  If someone has the potential and takes the dose, there is a higher chance of deviation.''



``But you were fine with doing it to others,'' Sveta murmured.



``Natural powers tend to fall more in line with the subject's nature,'' the Doctor said, ignoring Sveta.  ``Complimentary to their personality, their needs, and so on.  Better to leave that door open, in case it comes down to it, or to retain the ability to take a vial at a crucial juncture.''



``I believe,'' Lung growled, his voice strangely thin despite his size, with his partially healed injury, ``this would be a good time.''



``He's not moving,'' Canary said.



``His attention is consumed,'' the Number Man said.  ``We're insignificant, compared to\ldots this.''



``A healing power,'' I said.  I watched as Scion reached out for another vial.  He held it next to the one he'd already retrieved.



I could almost sense something from him.  Confusion?



``There aren't any healing powers,'' the Doctor answered.  We continued backing away.  ``When they crop up, it's a fluke, pure chance, an extension of another ability with a different focus.''



``A tinker power,'' I said.



``A tinker power would take time,'' Cuff said.



``A tinker power would be flexible enough to cover multiple bases,'' I said.  ``One of which could potentially get us out of here.''



``Perhaps,'' the Doctor said.  ``But I would like to remind you all what happens when someone undergoes their trigger event, natural or induced.  You would be rendered comatose.''



``My dogs can carry us,'' Rachel said.



``Point conceded,'' the Doctor replied.  We were moving faster now, with Scion not making a move.  ``But there is another concern.  The trigger event might draw his attention.''



\emph{Which would spell out our deaths}, I thought.



``Let us put some distance between ourselves and the being,'' the Doctor said.  ``One thousand feet seems like the safest bet.''



\emph{A thousand feet}, I thought.  ``Is this safehouse even that big?''



``Certainly,'' the Doctor said.  ``William.''



``Doctor,'' Manton said.



``I'm going to ask you to position Siberian up here.  We'll see if she can do any damage.''



``Yes,'' Manton agreed.



The Siberian stepped forward.



Manton leaned over and gave her a kiss on the cheek.



\emph{Out of sync.  Doesn't fit.  Like Number Man was complaining about with his clones}.



But I was happy to have \emph{someone} expendable standing guard.



We turned to leave, and I used my bugs to watch the scene, perching them around the Siberian, turning their cloudy, distorted senses on the golden man.



I could infer, rather than see, that he dropped a vial.  It hit the ground and shattered, the contents splashing out onto the ground and the walls.  He reached for another.



He held it for only seconds before letting both of the vials in his hands fall and shatter on the concrete floor.  He rose in the air to float over the mess, reaching out for more vials.



``Here,'' the Doctor said, as we reached the next floor.  ``\emph{These }were the vials we were trying to find.  I sent Contessa to find recipients for each of them.  I kept only three.''



There was a table with the vials set in what appeared to be a centrifuge.  The liquid inside was nearly black..



``Why these?''  I asked.



``There is a foreign agent in them.  The entity altered each power he granted to give them certain restrictions.  No power would be able to truly affect him, no power would cross the boundaries he set in dimension, or in affecting other powers.  There are no alterations to the elements in \emph{these, }only to the accompanying abilities, or complimentary powers.  The powers granted from \emph{these} vials don't cause the recipients to forget the visions they see.  Eidolon was one such case.  The extreme deviant cases on the special containment floor make up much of the remainder.''



``Extreme deviants,'' Sveta said.



``I'll need to dilute this, or I'll be no use to anyone.  The Balance formula, Number Man?''



``Where?'' he asked.



``The fridge,'' she said.  She leaned over the table, gazing at the vials.  ``Extreme deviants.  Some had only a trace of the foreign element, which we discovered later, others had known quantities.  Others\ldots perhaps they received some and we weren't aware or able to check after the fact.  Deviants like our friend in the ball here--''



``Sveta,'' Sveta said.  ``Garotte was the name you gave me, when I refused to take one for myself.  I was recipient one-six-one-six.  And I'm not your friend, Doctor.  I like to think the best of people, but I think you're far, far gone.''



``--Sveta,'' the Doctor said.  ``Deviants like \emph{Sveta} are a rare thing, particularly with the Balance formula in the mix.  Extreme deviants form a subset within a subset, with physical mutations that go well out of bounds of any solid reference point we have here on Earth.''



``Why?''  Golem asked.



The Doctor took the vial from the Number Man.  It was clear.  She used a funnel and tongs to pour the contents of the clear vial into the darker vial.  Though both vials were nearly full, the mixture didn't cause any overflow.  The color found a middle ground.  A deep red.



She turned it around, then clamped it in between two rubber bumpers.  She hit a button on the side of the table, and it began shaking, like a paint machine.  ``Two minutes.  Best freshly shaken, so the layers don't separate.  William?  Status?''



``He's floating down the hallway, knocking the vials to the ground.''



``Time?''



``Rate he's traveling\ldots I'd say a few minutes.  Three or four.''



``We'll finish the mixing and then run,'' the Doctor said.  She stared at the vial.  ``This may be the closest you get to your revenge, Sveta.  I'm left with no choice, and chances are good I'll change physically, even with the Balance formula.''



``You keep referring to that,'' I said.  ``What is it?''



``I've come to believe it's the opposite of what we had with the foreign agent.  One power, or a collection of powers, calibrated in advance by the entity, with humans in mind.  By mixing it into other vials, we borrow this particular quality, at the cost of having more physical changes with any such power we grant.  We retain humanity more easily, safeguarding against deviant cases.''



``You found a way to collect powers,'' Golem said.



``In a sense,'' the Doctor said.  She sighed heavily.  ``You came for a reason.''



``I did,'' I said.  ``\emph{We} did.  For answers, for insights on the entity, and because we need Doormaker if we're going to win this fight against Scion.''



The Doctor looked at Doormaker, who was being held by two Harbingers.  ``We'd hoped to use Doormaker in conjunction with Khonsu, for a mobile force that could safely pressure the entity.  A last measure.''



``You had an awful lot of plans,'' I said.



``We did.  I can tell you about them, or I can answer your questions.  What information do you desire, Weaver?  What insights on the entity could win this for us?''



I swallowed.



``Second Triggers,'' I said.



The Doctor frowned.  ``Too many people have come to me about that.  It's a promise of more power that manifests just often enough to tantalize, infrequently enough to leave countless disappointed.''



``What is it?''  I asked.



``When powers manifest, they come with safeguards.  The same programmed safeguards that I seek to circumvent or ignore with these foreign agents.''  She tapped the desk.  ``The agent, the power, seeks to protect the host, so it prevents the host from harming itself.  It's a crude measure, one the agent applied with broad, general strokes.  Not every agent can receive individual attention, and the ones that do, I believe, were more hampered than not.  With the second trigger, the agent reaches out, makes contact with others, networks and draws on collective information to refine the restrictions and save its host.''



``Is it always around other parahumans, then?''



``Not always, but frequently.  Circumstances tend to mirror the original trigger event.  The resulting power ignores restrictions that were previously set.''



The shaking of the machine began to slow.



``You're involved with a lot of powerful parahumans,'' I said.  ``Do you have a means of causing second triggers?''



``We've done it for several clients in the past, with varying degrees of success.  Because of the time it takes, and the arrangements involved, we put a high premium on it.  We've had more clients die trying to collect the funds for this premium than we've had clients go through with the procedure,'' she said.



``A catch twenty-two, if you will,'' the Number Man said.  ``If you're powerful enough to have the necessary funds, then you don't need a second trigger to thrive.  If you need a second trigger, you lack the funds.''



``I get the feeling you didn't devote much attention to this,'' Golem said.  ``Why not?''



``Because reducing the restrictions that are in place only gives us a power that has \emph{less} restrictions, when we need powers with \emph{none}.  We needed to luck into a formula that had an applicable power as well as a whole, untainted foreign power within, and we needed it in a vehicle we could use, an individual without crippling mental, psychological, emotional or physical deviations.  Eidolon was that, and Eidolon had a fatal flaw in the end.''



I nodded, biting my lip.



``We should go,'' the Doctor said.  ``Where is Scion?''



``Still upstairs,'' Manton said, pointing at the ceiling, off to the right.  ``He's gone still.  He's got vials in his hands again.''



The Doctor nodded.  ``This way.  Just a little further down, and I'll ingest this.  With luck, we'll have a weapon or a way out.''



``What about these vials?''  I asked.



``The powers wouldn't help.''



``If they're special, if they could give us an answer--''



``The powers are poor,'' the Doctor said.  ``Foreign, yes, but poor.  When we tested these, we got a defensive power utilizing warped space and a power that allows one to take over a nearby parahuman's mind, body and powers automatically on death.  The one I hold should have attack or mover capabilities, if not both.''



She input a code by the door, and William Manton set about opening it.  Another wheel-lock.



``What would happen if a person with powers drank one?''  I asked.



``Nothing at all,'' the Doctor said.  ``Believe me, we've tried hybridizing natural and Cauldron capes.  You might as well drink water, for much the same effect.''



I nodded, but I didn't take my eyes off the table.



``You hoped for a way to increase your powers?  Or the powers of everyone here?''  The Doctor asked.



``Yes,'' I said.



``Downstairs,'' she said.  ``We'll see.''



I nodded.  I used my flight pack to travel down the stairs more quickly.



Ever downward.  Descending.



``He's coming,'' Manton said.  ``There's nothing left between us to slow him down.  I'm- the Siberian will fight now.''



The Doctor nodded.



I could sense the two meeting.  The Siberian dashing forward.  Scion apparently uncaring.



The Siberian cleaved deep.  The way her body intersected Scion, it was like ghosts fighting.



\emph{Tattletale says he closes wounds as fast as they appear, so fast our senses can't perceive it.}



If that was so, the Siberian was doing horrific amounts of damage.  She passed bodily through him, and glowing motes followed her as she emerged on the other side, landing and wheeling around.



``Intersect him,'' I said.  ``It'll burn through his reserves.''



Manton nodded.



``Number Man,'' the Doctor said.  ``The--''



``EM readers?''



``EM readers.''



The Number Man ducked into a side corridor.



``This is it,'' the Doctor said.  She pointed down.  ``The last room.  Lowest room in the complex.''



I could see it, a flight down.  A heavy door, vaultlike.



``Then it is a dead end,'' Lung rumbled.



``Fuck,'' Imp said.  ``Fuck it, fuck damn shit.''



We reached the door, and Lung set his claws on the wheel to open the door.  He'd just started turning when the Number Man appeared, a paddle-like wand in each hand.



Manton took one of the paddles.



The Siberian was standing in the middle of Scion, their bodies overlapping.  If her presence tore into him, then every passing fraction of a second was a good one-hundred and some pounds of flesh being eaten away.  Depending on how fast he regenerated, it could be vast quantities.  Turning a strength into a weakness.



But he didn't seem to care.  He floated there, his back turned to the doorway we'd used to travel to the next floor down, staring at the rows of vials.  Uncaring about the Siberian's sustained assault.



``He doesn't care,'' I murmured.



The Doctor and the Number Man looked up from the paddle the Number Man had in hand.  He was apparently calibrating it.



``Scion doesn't care that Siberian's tearing him up,'' I clarified.



``Of course he doesn't,'' the Doctor said.  ``He's alien.  He doesn't have human feelings.''



``He's a force of nature,'' Number Man said.



I shook my head.  ``No.  Human feelings are why he's a danger.  Without them, he'd be some nebulous threat, three hundred years in the future.  But he's lashing out, trying to find himself, and that's why he's dangerous.''



The Number man waved the wand around my head, then frowned.  He waved it around his \emph{own} head, read the digital display, then tried the Doctor.  He tried waving it at Lung, but Lung swatted at it.



``He's alien above all else.  Abstract.'' the Doctor said.  Her eyes fell on the vial.  ``It's through alien, abstract methods we'll defeat him, if it's even possible.''



``The door is stuck,'' Lung said.



``The way the column has settled may have put undue stress on this part of the architecture,'' Number Man said.  ``If you'd let me--''



``I know,'' the Doctor said.  ``If I'd let you have a hand in designing this\ldots but you were new to the team.  I didn't yet trust you with sensitive matters.''



Number Man nodded, taking it as something matter-of-fact.



Lung heaved on the door, putting all of his superhuman strength behind it.  It barely budged.



``Take her,'' Alexandria said.



Lung took Gully's body.



Alexandria pushed.  A crack appeared in the ceiling, dust showering down on top of us.



``Structural,'' Number Man said.  ``If we open it, it'll cave in on us.''



``This does not concern me,'' Lung said.  ``Stand back, and I will push my way through.''



Golem shook his head.  ``Eventually, but what about the time it takes to burrow through?  We can't afford it.''



The Doctor was looking down at the vial.



``If we're going to win this,'' I said, ``I want it to be because of \emph{our} strength, not an abstract one.  And I \emph{know} that sounds corny.''



``A nice sentiment,'' the Number Man said.  ``But I'm afraid that power you're digging for is out of your reach, Weaver.''



I looked at him.



``Or it's already \emph{in} your reach.  You can't have a second trigger because you already had one,'' he said.



I blinked.



``Given the signature, it's very possible you had two trigger events in quick succession.  Not uncommon.  The horror of manifesting your power, it prompted another trigger.''



``No,'' I said.  ``There's got to be \emph{something}.''



``If there is, a second trigger event isn't it,'' the Number Man said.  ``I can check your allies, but we can't do much more.  We used to rely on Contessa's power to determine the exact event needed for a second trigger.''



I nodded numbly.



``I'm sorry,'' Imp said.



I shook my head.  I'd staked hopes on this, despite promises to myself that I wouldn't.



Beside me, the Doctor removed the black rubber cork from the vial.



The Siberian appeared beside us in the same instant.  Manton spoke, ``He finally took action and struck my Siberian.''



I could sense Scion above.  Staring at the corridor with the vials.



He reached out, and a golden light flared.  It was like a flicker of the lights, and it was so vivid I thought for a second I was seeing it with my \emph{own} eyes.



The vials each shattered simultaneously.



Glass and fluids rained down onto the floor.  My bugs were swamped all along the corridor.



Scion moved, killing my bugs on contact as he headed down to the next floor.



With my bugs, I could sense Number Man letting the wand go.  It clattered to the stairs below him.  ``Broken.''



\emph{Broken}?



Lung created flame for us to see by.



The Doctor stood there, her hands mangled where she'd been holding the vial, bleeding wounds at her throat.



``Your hands,'' Manton said.



She shook her head.  ``S- superficial.''



There was a pause.



``Did you drink any?'' I asked.



She shook her head.  ``Barely any.''



I looked down at the stairs.  \emph{Lap it up}?



No.  Something Skidmark or Newter had said, once upon a time.  My first introduction to the vials.



And she'd said she needed a \emph{whole} power.  Would a partial dose only give half a power?  A distorted one?



I could only guess.



``Okay,'' I said.  ``Siberian\ldots make us a path around the door.''



Manton nodded, as if I'd talked to him.  Siberian walked into the wall, her power crushing stone.  The rest of us moved up the stairwell, closer to Scion.



``Guys,'' Imp said.



Lung had to move to cast the light on her.



She held Sveta's sphere.  Fractures marked the entire surface, and they spread with every passing second.



I withdrew my crystal-encased knife.  ``Lung?''



He took hold of it with one hand, nearly singing me with the heat of the flame that had surrounded the limb moments ago.  He crushed it, winced as the knife ate through the claw at the end of his thumb.



I gingerly took hold of the knife, switched the settings to remove the disintegration effect, then started it up again.



It took a full four seconds.  The calibration was off, stuff clogged.  Not a big surprise.



``Halfway,'' Manton said.  ``No sign of collapse.''



Scion appeared at the top of the stairs.



Leaving us without a place to even run to.



``A third trigger event,'' I said.  ``Is it--''



``No,'' the Doctor said.



``There has to be a way.''



``There isn't one,'' she said.  ``You have the power you have, nothing more.''



``Okay,'' I answered.



``Hey,'' Imp said, ``Your power isn't the only one that's shit in this circumstance.''



The orb bucked, the fracturing doubling in quantity.



Then it broke.



Sveta hit the ground, and then unfurled.  Tendrils extended up the stairs, encircling Scion.



``Focus on him,'' she said.  ``Oh god.  Focus on him.  It's him and me, we're the only people here.''



The others were disappearing into the tunnel.  Rachel, Imp, Canary, the Doctor's group\ldots



``Can't\ldots'' Sveta said.



The Doctor headed into the tunnel.



A tendril encircled one of the Doctor's ruined hands.



The Doctor screamed.  I could hear bone breaking, see blood welling around the thin tendril of living razor wire.



Sveta's tendrils continued to extend, stretching out.



Each one chose the Doctor as the mark.



``Had to pick someone,'' Sveta whispered.  ``Couldn't focus on him alone.  I'm sorry, but you're the best choice.''



The tendrlis found points closer to the Doctor's midsection, crushing.



The Doctor's screams became strangled.



Sveta coiled around the Doctor, burying the woman beneath overlapping tendrils, until there was a cocoon and a girl's face, curled up on the stairs.  Blood pooled beneath them.



Scion continued his approach.



I held my ground, forming swarm-decoys.  They hadn't worked last time,  but-



Nothing.  He walked past them.



I held my knife, waited as he closed the distance, standing in his way.  I slashed at his throat, dragged the blade along his chest.



Smoke rose, billowing in quantities I couldn't have imagined.



He pushed me aside.



Walking towards the door.



I realized what was about to happen.  My mind was all noise as I screamed out a warning using my swarm, telling the others to get away.



I reached out and grabbed Sveta's face, the point from which all the tendrils extended.  An action carried out in panic.  I felt a tendril or two wrap around my forearm.  Hand and arm obliterated.



\emph{I just got a new one}, I thought, almost dazed.



Scion pushed his way past the door.  The door that was bearing the load of the ceiling above us.



Sveta dropped the doctor, and I felt the tendrils brush past me, ensnaring bugs.  Then they snapped out, grabbing the door at the top of the staircase.



In the next instant, we were pulled to the door, virtually thrown.  I used my flight pack to try and break the fall, to stop from being turned into a smear, but Sveta caught the brunt of the impact, webbing out to ensnare our surroundings.



The ceiling came down.  A whole section of the substructure, apparently damaged, cracked by the fall or by some native impurity.



The dust settled.



And I saw what Scion had come for.



His partner.





