





The stairwell was buried under chunks of concrete and steel large and heavy enough to flatten trucks, but the ceiling was high, and the gap in it gave me a view of the chamber beyond, lit by the red emergency lights.  My view of Scion was obstructed by the rubble on the stairs, but I saw the golden glow that he cast off.



He was so small, so far away.



The \emph{partner, }so massive.



The room looked like an aircraft hangar.  My bugs reached out, and I could only sense the three walls closest to me.  Vast.



The partner filled the space, beautiful in a way I struggled to put words to.  It was like a volcano mid-eruption, stone mingled with the orange-red magma, spray or smoke reaching incredible heights\ldots it was breathtaking in the sheer elemental nature of it, fascinating, beautiful, and so incomprehensible I couldn't have understood it with decades of study.



But where the volcano was driven by seismic movements, I was pretty sure, and the storm by wind, this was driven by something else.  Just as basic, on a level.



An \emph{idea}, half-formed, captured in a moment.



It conjured up images an artist's sketchpad, putting body parts on the page, trying variations.  There, in the sliver of the chamber I could make out, there was flesh, a soft gray, lit by the red emergency lighting.  It might have been menacing, but the lines had a softness to them, and every part was positioned in an almost gentle manner.  The individual parts were androgynous, as a rule, but they veered into the slightly masculine, the slightly feminine, even \emph{alien}, territories.



Always, there was something to take the threat out of it.  One long-fingered hand, upturned, pinky and ring fingers curled slightly, as if reaching down to offer aid.  Another hand, more childish, the underside and palm white, before fading into the gray colors the other parts shared, vulnerable like a dog with its throat or belly exposed.  Another still, with water running down it, streams of the liquid running between and down fingers, more a piece of art than a limb intended for use.  There were countless more I couldn't see, couldn't spare the bugs to study them.



I could look at any one piece, and I could see the beauty in it.  Any number of these could have been blended together, mixed and matched to create a human being.  Not overtly male or female, but no doubt \emph{kind} in appearance.



Then, at the same time, there was the bigger picture, only a glimpse of it in the far end of the staircase, through the part of the ceiling that had collapsed in that massive room\ldots this \emph{jungle }of flesh, like parts of a doll waiting to be assembled.  Artificial, everything in the wrong scale.  There was a pattern to it, like there was a pattern to the movement of the waves in the ocean storm, but I didn't have access to the underlying logic.  I could only get a general sense of which direction the wind had been blowing.



Here and there, flesh connected to flesh.  In other places, the flesh broke down into core elements, expanses of skin, veins, muscle and bone, all with hints of the same art of experimentation the larger pieces had.  Where flesh didn't connect to other pieces, it broke down further into other things, into fractals and patterns, then into things or spaces I couldn't make out, like it had turned around a corner that didn't exist.



Sveta released of my forearm, and the resulting pain hauled me out of an awestruck daze.



Her tendrils found targets with a speed my eyes couldn't follow, and she wrapped herself around the table that had held the vials.



It took a moment before \emph{every} tendril was set in place.  When she was done, she let her head sink down until her face was pressed against the tabletop, her eyes shut.



Blood ran down my mangled arm, soaking into the fabric of my costume and then oozing out slowly at points where the skin was tightest against the surface.  Normally, it might have been my knuckles, my forearm.  Here, it was the parts that hadn't been wrapped by the tendril, bulging out.



At the very least, the armor on my costume and the nature of the fabric had kept the tendrils from simply slicing through the flesh like razor wire.  The \emph{armor }was mangled, but it had saved me a severed artery.



I felt the limb throb, as if it were responding to the fact that I was paying attention to it.  It made for an eerie sensation, where the dull sensation felt so out of tune with the degree of injury, yet so great, compared to the little that remained of the limb.



``\emph{Shit},'' I said.



``Don't,'' Sveta said.  ``Don't move, don't talk.''



I went still, even as the dull throb in my arm got worse.  I was losing blood, though not as much as I thought I should be.



\emph{Better than one of those things going around my neck.}



``Don't move, don't talk.  You're not there,'' she murmured, barely audible.



My eyes moved to the stairwell and the scene below.  My teammates were there.  Lung and Canary were as well.



``The only ones here are me and my thoughts,'' Sveta said.  Her eyes were shut.  ``I am in control of my mind and my feelings, and I am focused.  I am confident, and I am building towards a better future for myself.  Every success is a component in building that up, a brick on a building in construction, but my mistakes do not tear it down.''



The stand she was wrapped around creaked.



``My mistakes do not tear it down.  They are a part of me, but they are not the most important part of me.''



\emph{Hurry}, I thought.



Uncharitable, maybe, but I couldn't afford to sit back and bleed to death while she worked through this.  I \emph{understood} that she had her problems, that control was hard to come by.



I got that, but my friends could die down there, if the collapse hadn't killed them already.



Sveta let go of the table.  Her tendrils extended into the air around her, like a sea anemone's fronds.  Here and there, they touched things and snapped into place with a destructive power: the refrigerator that had held the Balance sample, a shelving unit, a countertop with drawers in front..



They caught on the bugs in the area, and they extinguished my swarm with an almost ruthless efficiency.  Too many tendrils for my bugs to navigate between them, the movements too unpredictable as they drifted in the air, responding to air currents.  The tendrils were severing steel handles on the drawers, a bug's flesh was nothing.



\emph{My} flesh was nothing.  The longest of them came dangerously close to making contact with me.



``I'm going to leave,'' she said.  From the tone and the volume, she was talking to herself, trying to convince herself to move.



\emph{To be a bystander in your own body}, I thought.



I felt a more serious pain building in my arm.  Something more representative of the damage that had been done to it.



``I'm going where there aren't any people,'' Sveta said, again.



\emph{Go}, I thought.



Tendrils found the ragged edges where the ceiling above the stairwell had cracked.  Sveta launched herself into the stairwell as though she were a living slingshot.  Tendrils splayed out in every direction to stop her forward momentum, arresting her nearly as fast as she'd moved.  Then she reached out again, and was gone into the morass of body parts below, with its dim red lighting.



She was gone.



Yet I couldn't bring myself to move.



The pain in my arm had me rattled.  It was intense, yet disconnected in a way.  An alarm system that wailed with lights flashing, but it was somewhere off to one side, in another room somewhere.



I didn't want to be in a metaphorical room with that pain.  The second my blood started pounding, the moment I set my foot down to run and an impact reverberated through my body, this sharp, violent pain would become something else entirely.



Instead, I activated my flight pack.  To get myself moving, I pushed off the ground, floating into the stairwell.



When I reached the first chunk of rubble, I set one foot on it and drove myself forward, with as smooth and gentle a motion as I could manage.  The flight pack managed a decent speed, but any help was a good thing.



Another chunk of rubble, another kick forward.



More of the room below came into view.  The staircase was as long as it was because the impossibly large room needed a high ceiling.  Now I was getting the full view, rather than a sliver of it all, coupled with the input from my bugs.  I could see just how much of the partner's flesh filled the space, flooding whole areas, interlocking or simply arranged side by side.  Nearly three stories high, and many of the parts reached from floor to ceiling.



I pushed my swarm through the space, and I could feel a kind of disorientation.  Something I'd experienced before, in mild doses.  I directed my bugs from points A to B, except they only made it partway, or they moved too far, or they arrived at a slightly different location.



Ominous.



And it wasn't the only thing that caught my attention, as I increased my speed, descending towards Scion and the others.  There was a creaking noise.  The groan of a structure settling, of tired floorboards and hinges in dire need of oiling.



It didn't stop.  I couldn't tell with my ears, but my swarm had a range of hearing that extended beyond the human spectrum.  Through that distorted sense, I could tell that there was a sound that was gradually getting worse.  A screeching, tearing noise.



At my command, bugs moved away from the second entity, away from Scion and the rubble, and they headed \emph{up}.



The combination of fine sensory input and the hundreds of bugs told me the tremors were worse in specific spots, the cracks deeper in spots.



It formed a map of sorts.  Where the cracks were, the tremors and creaks, areas stood out as danger zones.



I passed the patch of blood and mangled flesh where the doctor had fallen.  Some of the tendrils had crushed their way through bone, severing the skull in half.  Others had found their way into the cracks between joints, sawing through connective tissues, muscle and skin to completely detach the limbs.  If any part of her had still been alive, the rubble had crushed it when it had fallen.



I accelerated my forward momentum with another gentle kick.



Chunks of the ceiling dropped.  I didn't slow, only using the senses the bugs offered along with the flight pack to move out of the way well before they could reach me.



As I'd done with the rubble, I kicked off a falling section of the ceiling, to better change direction and propel myself forward.



I found the others.  Golem was almost invisible as he created hands of concrete to shield himself, Cuff and Imp.  I'd nearly mistaken his hands for one of the false ones.  The only difference was that his hands moved, for a little while.



Rachel had an unconscious Canary slung over her lap.  Lung had foregone riding Bastard to run on his own, loping forward on all fours, climbing more than he ran.  It was too hard to move through this labyrinth, where the pale gray flesh occupied as much space as it left untouched.  Easier for Lung to lunge forward, grab an empty eye socket, then leap forward onto an outstretched arm.  The dogs found solid surfaces to leap onto and away from.



The Number Man, Alexandria, the Harbingers, the wounded and the captured case fifty-threes were in another group.  He'd found a spot he deemed safe from the collapse, beneath an arch of tissue.



The materials that were falling were all substantial, pieces of granite bigger than a truck, concrete shelves, panes of solid steel torn at the edges where stress had brought them free.  The impacts were heavy enough I could feel the shockwaves in the air.  It made my arm move, which renewed the pain, reminded me of the blood loss and what was very possibly catastrophic damage.



I felt an edge of panic.  Not a familiar feeling.  It wasn't being \emph{hurt }that was the problem, but the amount of attention it was occupying.  I needed to focus, to pay attention to any number of things, and yet my arm kept screaming for me to fix it.



Why had I touched her?  I hadn't been \emph{planning }for her to save me.  Hadn't even been aware she could.



A distance away, a chunk of concrete fell atop Scion.  He barely reacted to the blow itself, but he lashed out.  A controlled blast, very carefully avoiding contact with his alter ego, simultaneously obliterating much of the offending material.  I could sense the others splitting further apart as the blast brought more of the architecture down around them.



Scion rose into the air, floating deeper into the room.  As he'd done with the vials, he touched the flesh beside him, almost tender.



I drew closer to the others, carefully navigating between the fractal webs that the tissues seemed to emerge from.  My bugs helped pave the way, checking where the routes were best.  Again, the bugs' trajectories seemed off.  A few flew into the fractal spaces, and subsequently dropped off my power's radar.



I was caught off guard when my path veered unexpectedly.  It had been safe for my swarm, but it led me off course, the entire room seeming to swing as the bugs on the ceiling and floor moved and I seemed to stay still.  I found myself on course for a fractal `hedge' that bordered the top edge of a large eye.



I was already readjusting, carefully guiding myself towards safer open space.  If I hadn't had the benefit of my swarm, if my reflexes had been slower, I might have collided with it.



I wasn't entirely sure what might have happened if I had, but something that put my bugs well beyond my reach couldn't have been good.



The near-miss was making my heart pound.  It wasn't something I would have paid attention to, normally, but now it was impacting the damage to my arm.  My entire body was starting to ache, as though the nerves in and around the injury site itself couldn't host it all.



I couldn't calm down, so keeping my actions low-key and maintaining a low heart rate wasn't helping as much.  I increased my pace a little, using a bit more force as I propelled myself forward.



Bastard barreled through a shelf of skin, muscle and a rigid, rubbery material that might have been cartilage.



\emph{Soft, breakable, }I thought, as I changed direction, following, moving lower to the ground.



I might have said the idea dawned on me, but \emph{dawn} implied light, the rising of the sun, the start of a new day.  This was something else.  The notion\ldots \emph{descended} on me, that I was seeing what Tattletale had talked about.



She'd called it the well.  Scion was only the tip of the iceberg, any damage to him drawing from the well to fix his physical body.



This was it.  The other entity, it had never established the separate self, independent of the well.  Something had gone wrong.



I thought about what Cauldron had said, about having already saved the world.



\emph{They fought this thing before and they beat it}.



The collapse was dwindling, but it was dust and finer rocks that were falling, now, billowing through the space.  Just as scary, on a level, and it was hurting visibility.



Rachel, Lung and the canines tore through a barrier I'd thought they would take the time to circle around.  My course had been plotted to put myself in their way, and now I threatened to fall behind.



Instead, I dropped down, taking a steeper course.



No, they were moving too fast.  I was going to land on top of Lung if I maintained the course, instead of landing in front of them.  And that was if I didn't slow down before hitting the ground.



I maintained the course.  I didn't slow down.



Instead, I tried to shout out a heads up.  \emph{He has enhanced hearing}.



``Lung.''



My voice wasn't as loud as I'd hoped, and I was drowned out by another shower of dust and debris.



The only reason I didn't hit him hard enough to break \emph{one} of our necks was that he stopped to grab two fingers in the midst of our surroundings, tensing to throw himself forward.



I landed two feet in front of him, twisting myself around to avoid letting my arm hit the ground directly.  The vibration shuddered through my entire body and increased the pain a hundredfold anyways.



I was left barely able to breathe, writhing on the ground, my arm crushed between my thighs and my stomach, because squeezing it and applying pressure like I was proved a fraction less painful than letting it move on its own.



And Lung loomed over me.



``Ah--''  I managed, before I found myself huffing out the remainder of my breath.



``I have no reason to help you,'' Lung growled the words, nearly inaudible with the sounds in the distance.  His voice was altered with his transformation, slurred.



I couldn't muster a response, slurred, audible or otherwise.



``I think you have lost a lot of blood.  You will slip into a state of shock, Skitter.  Your body will betray you.  You will piss and shit yourself.  Your emotions will escape your control and you will experience a kind of terror that you might think is not possible.''



I grit my teeth.  I knew Rachel had stopped nearby, but Huntress was acting agitated, and Rachel couldn't get control.  A part of me wanted to draw the connections, interpret \emph{why} Huntress was pacing like she was, and I found it harder than it should be.



``I dislike the idea of being a follower, little Skitter,'' Lung rumbled.  ``I maintain a territory, always.  I bring my enemies low, and I am feared and respected, always.  I enjoy the things I enjoy, drinking, food, fucking women.  Never being fully out of control.  You understand?''



\emph{This is my fate}, I thought, a little deliriously.  \emph{I die getting monologued to by a supervillain}.



``A man told me that in\emph{ Go}, it is deemed more worthy, more honorable, more respectable, if you can accept the fight as lost and surrender.  If you are right, if it is at the right moment.  I came with you because I knew I would not beat him in another fight.  Here, there is something I can do.  But I do not follow you, I do not give up that control.  I would say partners, but I would be lying.''



I did what I could to meet his eyes.  I still had Defiant's knife in my hand.  I deactivated the blur and let it fall.  Then I reached over to my elbow and used all of my strength to raise my injured arm.



It flopped like a spaghetti noodle, the bones simply not there, pulverized.



Lung took my arm in one claw, gripping it hard.  My back arched, my chest expanding as I drew in a ragged breath.  I held in the scream that I so badly wanted to utter.



``I fight \emph{him} because it is my nature.  He would sunder me without thinking.  He humiliates me, destroys any place I would call territory, and would deny me the things I enjoy.  Good food, some drink, fucking.  I will not bow, understand?  I will not ever \emph{lose}.''



My vision was swimming.  I wasn't even sure if I was maintaining eye contact, now.



He squeezed a little more.  I refused to scream, but I had to utter \emph{something}.  I settled for a low groan, an extended grunt, strangled.



``You cannot hold yourself straight.  You are weak enough that to be alongside you would bring me lower than I stand now.  You understand?''



\emph{Like Grey Boy, turning on Jack because Jack failed and showed a degree of weakness}.



``Skitter,'' Rachel's voice sounded.  ``Problem?''



She'd come.  She wasn't positioned to see my hand.



``Go,'' Lung growled.  ``Tell her you need help.''



I drew an `x' in Rachel's way, with the handful of bugs I had on hand, barring her path.



``You came to me.  None of the others.  Not Bitch, not your heroes, not even the men and women from Cauldron.  You want my assistance.  Ask me for it, show me your weakness.''



\emph{Cauterize the limb}, I thought.  It wouldn't \emph{fix} anything, but there was no way to stem the blood loss from the damage that extended across the limb.  Any tourniquet capable of cutting off the blood flow would make the limb fall off anyways, and then I'd \emph{still} have blood loss.



At best, if I were to ask him, he'd be gone.  The not-partnership would be over the second I admitted my weakness.  At worst, he'd kill me.



I didn't have enough wind to say much.



``\emph{I'll kill you},'' I gasped out the words.



He didn't react, except to squeeze the arm harder.  Again, my back arched.  I writhed, gritting my teeth.



``With a trick?  Deception?  By asking for help?''



I shook my head.



He reached down and picked up the disintegration knife.  ``With this?''



I shook my head again, and immediately regretted not having spoken instead.  My vision swam.  I had to fight to keep my eyes on his.



He didn't follow up with another question.



\emph{Come on}, I thought.  \emph{Can't hold eye contact}.



``Mm,'' he grunted.



``Burn it,'' I said.  ``If you're angry\ldots''



I had to stop to get my breath.



``Angry?'' he asked.



``Me beating you\ldots twice\ldots then enjoy burning me\ldots but fuck\ldots fucking burn it off.''



There was a long pause.



He lit his hand on fire.  My mangled arm went up in flames.



I broke eye contact.  I might have screamed.  I wasn't sure.



\sectionbreak



Only a minute, judging by the way things had moved.  Darkness had swept over my vision, I'd blacked out for a moment.



Arm gone, stump burned black.  I was draped on Huntress' back, behind Rachel.  Canary was slumped over in front of her.



My entire body hurt in a steady, consistent way that suggested it wasn't injury, but the aftermath of the other trauma.  It was very possible my body was flooded with whatever neurotransmitters told it I was in pain.



I wasn't up to fighting my way to an upright position.  It might even be dangerous.



I'd started with a good number of bugs, but they'd been whittled down.  I had only a few thousand, now.



The ceiling had stopped falling down on us, at least for the moment, but the groaning and creaking continued.



It's the creature in here.  Scion's counterpart.  He's pushing against the walls of the structure.  It might even be why the walls distorted and why the door wouldn't open.



Huntress slowed, then came to a stop.  Bastard nearly sliced my face open with one of the spikes on his shoulder as he approached and stopped at Rachel and Huntress' left.



Rachel was looking around.



``They ran,'' Lung said.  ``There is nothing stopping them from retreating the way we came.  Scion is occupied.''



``Stairwell collapsed,'' Rachel said.



``I am strong, I could fight through it.  The dogs are strong as well.  Or we climb through a hole in the ceiling.  There is nothing left here.''



I began reorganizing my bugs.  Less need to keep them on the ceiling.  And I needed to find Scion, find the others and keep some here to give myself a stronger voice.



``\emph{No},'' I said, using the swarm to speak.  \emph{I} could barely hear myself.



Lung turned his head.  Rachel did too.



\emph{Good hearing}.



``You're awake,'' Rachel said.  ``Fucking tell me, did he-``



``\emph{He did good,}'' I said.



She fell silent.



``\emph{The others are here, and you don't need to climb through the hole in the ceiling.  You can climb over the rubble in the stairwell and still stand upright.}``



``Mm,'' Lung made a noncommittal grunt.



I continued speaking with the swarm, drawing an arrow in front of Rachel.  ``\emph{The others}.''



She whistled, goading Huntress forward.  Bastard and Lung followed.



Hard to manage the swarm, given the number of intervening obstacles.  There was so much here.  All an extension of the new entity.



\emph{This is the well.  This is what Scion looks like, when we see beyond the image on the surface}.  This is the sheer amount of flesh we need to destroy, when we do manage to get past his defenses.



But if that was the case, where was \emph{this} entity's other body?



We reunited with the others.



``Ah, here we go,'' the Number Man said.  He'd been joined by Golem's group, and they remained under the shelter.



``Holy shit,'' Golem said.  ``Weaver.  Your hand.''



He said it like I wasn't aware.



But I didn't respond.  My focus was on the swarm.



They'd found Scion.



He was floating opposite another figure.  A sexless human shape, with hair that was disproportionately long for its body, hanging beneath the point where one foot dangled in the air.  The figure was incomplete, fractals extending from portions of its back, of arms and one leg.



Two things hit me at the same time.



One of those things was that the odd, pattern-like kaleidoscopes of flesh and whatever else weren't \emph{terminus} points, but points where the limbs passed into another dimension.



The well was far deeper than I'd thought.  There was so much more to the entities than we were seeing here.



The other thought was that this was the other body.  It was the second entity's body, the part he would have shown us.



``\emph{Scion's} counterpart?'' I asked.  ``It was putting together a human body.''



``We saw it,'' Golem said.  ``Before the Number Man signaled us.''



Rachel helped me down.  Alexandria stepped forward to give me a hand.  Together, they eased me down.



The creaking increased, a sudden shift.  Dust showered down from every crack in the complex.



``I feel like a traitor for saying it,'' Imp said, ``But looking at this, hearing all we've heard, I'm sorta starting to agree with the Doctor.  Abstract solutions are looking a hell of a lot better.''



``\emph{We need to leave},'' I said, still using the swarm.



``All this trouble to get here,'' Imp said.  ``And then we go?  Madness!''



``\emph{No},'' I responded.



``I was joking.''



``No.  We came for answers.  This is it.  We \emph{had} answers.  Now we just needed to get in a position where we could use them.  Get them to Tattletale, to other thinkers.''



``And Scion?''



``\emph{Scion's occupied,}'' I said.



Scion was cupping the face of his counterpart.  The figure, no doubt grey skinned as the body parts that made up this area, was slack jawed.



\emph{He looked for futures where he'd find his counterpart}, I thought.  \emph{This was one of them\ldots just not what he wanted or expected.  Probably not even something he thought was possible}.



``\ldotsNot so easy to leave,'' the Number Man was saying.  ``The structure has shifted, rotated.  It's designed to, corkscrewing down over time and with any degree of force or movement.  It ensures the integrity of the panic room function, and it would have confused some of the first powerful non-Cauldron teleporters we were aware of.  The route you used to enter no longer leads into whatever corridor or entry point you used to break through.  We'd have to dig anew.  Even with the Siberian, it's time consuming.''



``This seems less than wise,'' Lung growled.  ``Burying yourself.''



``Frankly,'' the Number Man said, ``We expected that if we had to lock ourselves in down here, we wouldn't need to leave.''



``We should still go,'' Golem said.  ``And we should take something.  Chevalier made a weapon out of Behemoth and the Simurgh's parts.  Maybe we can do something with this?''



``It's human flesh,'' the Number Man said.  ``Or close enough to be of little difference.  There are powers contained within select areas, like threads of ore in a rock, and naturally there are some structural changes that set it apart from humans.  The thing was experimenting before settling on a body for itself.''



``You don't have a name for it?'' Cuff asked.



``I was only recently made aware it \emph{existed},'' the Number Man said.  ``The Doctor played things close to the vest.  I'd be open to suggestions.''



``Fuckster,'' Imp offered.



``It's not even a living thing anymore,'' Golem said.  ``It's more like a place, a garden or something.''



``Amusing you say that,'' the Number Man said.  ``We had a discussion with Lisette, the woman who proposed she could control him, and she said that the original name was Zion.  He named himself after a place as well.  We have theories on \emph{why}--''



Lung growled, interrupting.  ``I don't--''



Scion moved, abrupt.



``\emph{Silence,}'' I ordered, cutting Lung off in turn.



Scion's hand glowed as he reached down to his counterpart's neck.



He carved through his counterpart's flesh, severing the head.



``\emph{He's killing it.}''



``It's already dead,'' the Number Man said.



``\emph{He's killing it deader,}'' I said.



``Granted,'' the Number Man said.  He sighed.  ``There's nothing left in it.  She took powers it had probably planned to give to others, distilled them.  Then she dug in other places, and she took powers it needed to subsist.  It died and went still.''



``What the hell did she do \emph{before} that?'' Imp asked.  ``Have tea parties with it?''



Scion gripped the corpse, then rose into the air.



\emph{Everything} moved in response.  The entire room, shifting.  Every part dragging towards one central point.  Flesh disappeared into the patterns that hung in the air, patterns shifted, and parts emerged from others.  Pulled into invisible mouse holes and portals, pulled out of others.



``\emph{Fuck},'' the Number Man said.



I shifted position a little, reaching out to grab the healthy flesh closest to the burned stump, squeezing, as if I could make it hurt less.



``Fuck?'' Imp asked.



``The structure isn't going to hold.  Even with the reinforcements she put in\ldots no.''



``So?'' Rachel asked.



``When the walls break,'' the Number Man said, ``one million, seven hundred and thirty thousand tonnes of steel are going to drop on our heads.''



``Can we go out the sides?''  Golem suggested.



``Protected by the same water that's below us and to the sides, for the corkscrew operation.  Slow going at best, we get obliterated by pressurized water.''



I stared down at the ground.  My burn hurt so much I felt nauseous.  I also felt lightheaded.  Probably a side effect of blood loss.



``\emph{The Siberian},'' I said.  ``\emph{Protection effect}.''



``Can only protect a handful of us, less if you intend to move after things collapse.  Two hands, perhaps two feet, one behind.''



\emph{Only five}.



Five wasn't enough.



Scion had his hand raised over his head, the other entity held above, with masses of its flesh trailing beneath them.  My bugs told me the ceiling was arching slightly.  I could see where the ceiling met one wall, how a crack was forming along the edge.



``\emph{Ceiling falling,}'' I said.  I moved my arm to point, and I only wound up moving my stump, suppressing my reaction to the pain so I wouldn't provoke Lung.



Golem reached into the side of his suit.  A hand began emerging.



Too slow.  A full third of the ceiling over this room looked ready to collapse, and it was big enough and close enough to wipe us out.



Alexandria flew forward.  She caught the shelf of steel, concrete and granite.



Buying time, even as the slab continued to crack and break down where the stress of her holding it warred with the sheer weight and lack of support in other spaces.



Golem's hand propped it up, fingers curling around the edge to secure it.



I still wasn't thinking straight.



\emph{What's he doing}?



``Cuff, find me a piece of metal to use,'' Golem said.  ``The bigger the better.  And I'm talking \emph{big}.''



``The column?'' she asked.



``It broke up some, right?  Find me the closest, biggest piece.''



Cuff nodded.  ``Lung, Siberian, help us.''



Golem looked back at me.



``\emph{Go},'' I said.



He went without another word.



I was left sitting where I was, with injured case fifty-threes, with an unconscious Canary who'd apparently had a hand crushed, and a conscious, mostly unharmed Rachel and Imp.  We stared up at Scion.



``Well,'' Imp said.



He used his golden light to burn the other.  It coursed through the tissues, through the entirety of the thing.  An ocean of experimental features, of flesh and body parts.



``Well,'' Imp said, again.



I could almost sense a feeling radiating from Scion.



A hard emotion to name, if not a hard emotion to place.  I'd experienced it well enough.  Many had.



He was lashing out, destroying the remains, out of bewilderment, sadness, despair, anger, confusion.  All of it unfiltered.  The same emotion a child might experience with their first loss.  What a child would feel when they lost something irretrievable for the first time, when something was stolen from them and they hadn't prepared themselves for the possibility on any level.



It was what one felt as a child if they lost their dog, their home, their innocence.



Their mother.



``It's like when I lost Rollo, Brutus or Judas,'' Rachel said.



``\emph{Yeah,}'' I said.



``When my bro\ldots'' Imp said, trailing off.



\emph{How do you even articulate that?}  When he was broken?



``\emph{Yeah,}'' I said.



``Fucking \emph{good},'' Imp said.  ``I hope it \emph{sucks for him.}''



Together, we stared.  We watched Scion burn his partner.  Putting a torch to the garden.  Alexandria flew overhead to join the others, helping.



He dropped the remains, and they spooled out of some other dimension that the `garden' had spilled out into.



Golem began creating the hand.  The entire room shook as fingertips emerged.  Each a small building unto itself.  Cupping over, a protective barrier.



Nothing that would hold out against the kind of weight the Number Man had been talking about.



Then Cuff used her power, separating the hand in half, so it was the palm and four fingers.



I heard him say, ``\ldots\emph{Siberian\ldots this large}?''



``\emph{Yes},'' the Number Man said.



``Usually it's you with these plans,'' Imp said.



``She's hurt,'' Rachel said.



I grit my teeth, not taking my eyes off Scion.



No, that wasn't my excuse.



I was too focused on other fronts.  Not on survival\ldots fuck that.  I wanted to \emph{hurt} the bastard.  This was the best opportunity we had.  So long as the other entity was here, Scion was distracted.  Just like he was distracted with the case fifty-threes.  One chance to hurt him, possibly without retaliation.  Thinking of what we had on hand, what we \emph{could} have on hand\ldots trying to connect the dots.



Scion lashed out, sudden, unpredictable, raw destruction.



A section of ceiling in Sveta's general vicinity fell.  A whole section of the column above us was sliced off, falling.



I could see Sveta on the far end of the room.  \emph{She could help.}



I sent my bugs her way.



``\emph{I think I have something,}'' I said.



``Something?'' Imp asked.



``\emph{But we need to talk to the Number Man},'' I said.  ``\emph{See if it's doable.}''



Imp nodded, ``We'll get you on the dog's ba--''



I used my flight pack, lifting myself into the air.  My legs dangled, and I lacked the strength to keep my head fully raised.  My hair hung in front of my face.



Whatever.  Right now, at least, my body was an inconvenient puppet, a vehicle for my power and my brain, nothing else.



Fuck me, the burn hurt.



Rachel and Imp hurried to get the other injured on the dog's backs while I approached the other group.



The cupped hand turned monochrome as the Siberian used her power on it, then turned back to normal.  Alexandria lifted the hand, making room for others, for \emph{us} to get underneath.



I reached Number Man.  I spoke, and found my voice thin.  ``Your power.''



``My power?'' he asked.



``It's perception based.''



``I sense complex mathematics,'' he said.  ``Second nature to me.''



\emph{Ask a stupid question\ldots}



``Can you do controlled demolitions?'' I asked.



``Yes.  What are you wanting to demolish?''



``\emph{Everything,'' }I said.



He gave me a funny look, then glanced over his shoulder at the others.



He sighed.  ``Tell me what you need.''



``I need to bring it all down, and I need it to happen on my signal.  Can you figure it out?''



He nodded.  ``We can use Pretender.''



I turned my head, gazing at the remains of the `garden', slowly being consumed and reduced to motes of darkness by the golden light.



``We can use Sveta too,'' I said.  ``If she's willing.  Trying to figure out what we need to make this happen.''



``I'll need information,'' he said.  ``The layout, what exactly you want to happen, order\ldots''



``I'm not looking for anything complicated,'' I said.



I began illustrating the nature of the roof, where the cracks and rents were, and how deep they went.  I also began drawing out the remaining cords I still had stashed around my costume.  ``Cuff?''



``What?''



``Secure this thing.  We'll need a floor.''



``A floor?''



``\emph{Fast.}''



But I extended my focus to my bugs, at the same time.



My bugs reached Sveta.  She was pulling herself free of rubble.



``\emph{Sveta}.''



She looked around, confused.



``\emph{The bugs.}''



Her tendrils killed maybe sixty bugs as she focused her attention on them.



``\emph{It's Taylor.  Skitter, or Weaver.  Whatever you know me as.}''



She killed more before she got herself firmly secured to a large piece of concrete.



``Thank you,'' she said.  ``For getting me away from the collapse, before.  I didn't get a chance to say.  I'm \emph{really} sorry about your hand.''



\emph{``I'll get a new one if we make it that far.  Listen.  We're going to attack.  We need your help.''}



``I can't hurt him.''



``You can,'' I said.  ``\emph{Most definitely.}''



I drew an arrow.



``I\ldots \emph{what}?''



``\emph{Can you do it?}''



Sveta shook her head.  Or she made it sway, anyways.  ``But\ldots why?  And\ldots I don't think I can get away.''



``\emph{We just need a few seconds},'' I said.  ``\emph{He attunes himself to specific forms of attack, to negate them.  It's why the Siberian did as much damage as she did, earlier.  It's better if we can catch him by surprise, mix it up a little.  And if we do it here, now, before that corpse finishes burning, it should be easier to get away, because it clouds his senses like you\ldots}''



I wasn't sure what to call her.



``Monsters?  Victims?''



I'd always hated the use of the word victim.  ``\emph{Irregulars}.  \emph{It clouds his senses like the irregulars do.}''



Sveta's face changed.  I couldn't quite make it out with my bug vision.



``I can do it,'' she said.  ``I think I might even be able to do it and get away before he kills me.''



``\emph{It's not that.  Get into the hole in the ceiling we came from, before, if you can move that far, that fast.  The walls are broken, I can point a route.''}



She nodded.



``\emph{Thank you, Sveta.  Count this as another brick on that structure you're building},'' I said.



She didn't reply to that.



I looked over at the Number Man.  We were all underneath the barrier, now.  It wouldn't hold against Scion, but\ldots yeah.



``It's doable,'' the Number Man said, looking at Alexandria.  ``We need a signal.''



``Rachel,'' I said.  ``Whistle?''



She nodded.  Alexandria glanced at us for confirmation.



``One more thing,'' I said.



``What's that?'' she asked.



``I want you to swallow a fly.''



She arched one eyebrow.



``Or, better yet, hold it in your mouth.''



``I've lived with enough charlatans--''



``No joke,'' I said, serious.



She frowned, then opened her mouth.  I popped a housefly inside.



A moment later, she flew from the shelter.  Cuff began sealing the floor after her.



This was not an elegant plan.  Simple, crude.



``\emph{Sveta},'' I said.  ``\emph{Now}.''



She anchored herself on three different areas.  Then she grabbed the burning corpse.



She flung it at Scion.



\emph{Can't hurt him physically.}



Maybe emotionally\emph{.}



He reeled, perhaps a little stunned.



She hit him with more.  One after the other.



His hands glowed.



\emph{``Run,'' }I said, with my swarm, in the same moment I said, ``Now.''



Sveta bolted.  Scion attacked, a wide-area effect that scoured the room's interior.



Rachel whistled, using the only opening remaining.  Cuff closed it.



Outside, Alexandria charged in response to the signal.



She slammed into key points, where the structure was weakest.  I'd outlined some of it, the Number Man had inferred the rest.



\emph{Hitting him with the biggest thing available}.



We brought the column down.  One and three-quarter million tonnes, dropping down on our heads.



The cords were a measure that it turned out we didn't need.  The floor and Siberian's power sealed us off from the aftershock.  It sealed us off from almost all of the \emph{noise}, a hammer of solid steel the size of a skyscraper, striking an anvil.



I wasn't so optimistic as to think we'd \emph{killed} him.



But I could hope the impact destroyed more than one body.  That, like the `garden', there was a constant, steady connection, and the devastation could echo out through that connection and into the well.



\emph{``Whooo}.''\emph{  }Imp said, exhaling the word.



\emph{And now we wait to see if we die.}



\emph{Does he retaliate}?



\emph{Does he wipe us out, blasting his way free?}



There was only silence.



Of \emph{course} there was only silence.



And then I sensed movement.



A housefly, outside, approaching.



``Drop the barrier,'' I said.



Siberian did.  I could see everyone tense.



\emph{But it'd just deform the column above, nothing else}.



Alexandria, outside, tore the hand apart.  Lung and Cuff helped from the inside.



He'd blasted his way free, straight up.  Alexandria had torn away the flooring and the chunk of remaining column from on top of us.  Sure enough, there was a fist-indent in it.



``Whoooo!'' Imp whooped.  ``Screw you, golden man!''



I swayed a little, nearly falling.  Rachel caught me.



``You okay?'' Cuff asked.



I nodded.  ``\emph{Fuck me}, that was satisfying.''



``I will take your word for it,'' Lung said.  He held Canary.



``Aww, he's upset he didn't get to play a part,'' Imp mocked.



I looked at Lung with Canary, my eyes roving over our assembled number.  Ideas falling in place.



``Except,'' Golem said, morose, ``He's \emph{pissed off}, now.''



``Pissed off is something we can use,'' I said.



``A solution?'' Number Man asked.



I shook my head.  ``But I think, now, I know what it'll look like when I see it.  Hospital next.  I'll explain on the way.''





