





Two parts to a whole.



This, as everything does, builds towards the ultimate objective, a propagation of the species.



To rise above a competition among one's own species is a kind of transcendence.  Cooperation, a goal that extends beyond one's lifespan, one's community.  This entity can recall the moment of transcendence, the unification and reinvention of their species.



Everything extends to an end goal.  A complete and total mastery of all things.  In time, just as they spread and consumed their entire world, they will fill every space in all accessible universes that can be occupied.  In time, they will reach a stasis and they will fall from their transcendent state.  They will descend into competition once more, and they will devour each other alive once again.



Hope, continued existence, is dependent on another reinvention of their species.  They will use knowledge gleaned from countless other species, from mingling, matching and culling their own internal libraries of functions.



There is only so much time.  Only so many generations and cycles before things approach their final state.  Information will be exchanged, their species will weigh everything based on merit, and then they will seek a solution.  A final expenditure of power, a resetting of the universes, a reinvention of existence, or something beyond this entity.



This is the goal.  The most must be made of every cycle.



Two parts to a whole.  The other entity is a warrior, direct, oriented in the short-term goals.  This entity looks further, consulting possibilities.



Their general destination is in mind, and has been in mind for some time.  Already, they have begun to close their helix spiral, drawing fractionally towards one another with each rotation, controlling the pattern and timing of their approach.



\emph{Destination, }the Warrior entity communicates.



\emph{Agreement}, this entity responds.  The signals that accompany and form the overarching messages allow them to pick out sub-worlds for themselves.  Arrival points, destinations for critical shards to root, hosts for the extensions of those same shards.



\emph{Trajectory}, the other entity communicates.  More data on where they will arrive, the way they will move on approach, the placement of less crucial shards.



\emph{Agreement.  }This entity sees the constant messages as a distraction.  It is reorganizing, calling on its own precognition and clairvoyance to map out their actions after arrival.



This entity reforms itself, adjusting the placements of individual shards, priming itself for a deeper simulation, considering possible ways things can be carried out.



This takes time.  Focus.



\emph{Colony}, the other entity signals.



Narrowing down possible destinations.



\emph{Agreement}, this entity is distracted in responding.  It is receiving another broadcast.



A third.



The communication is almost alien, a member of their species, but long distant, from countless cycles ago.



It hesitates, then signals its own location.



\emph{Exchange}.  \emph{Meet}.



The response is garbled.  Takes time to analyze.



The third entity travels more through momentum than by insinuation.  It expends vast quantities of power to change course.



They meet violently.  As their ancestors did, they share with one another in a violent fashion, crashing together, breaking shard from shard.



This entity knows right away that there is a wealth of information here.  But there must be cooperation, information given for information.



Even as they grind together, destroying one another in a brutal exchange of shards, the entity works to salvage key shards, to put ones it can afford to lose on the exterior body.



This is the optimal path, the best way to achieve their end goal.  The shards here are rich with memories, experience and unexplored possibilities.  It is worth sacrificing as much as she is.



They break apart.  The third entity continues its path, moving to a distant star, its path perpendicular to the pair's.



\emph{Concern}, the Warrior entity expresses.



\emph{Confident}, this entity responds.  This is optimal.  It is heavy with these new shards, drowning in knowledge and experience.  If this could occur with every cycle, bringing this sort of information into the pattern, then survival beyond the endpoint would be virtually guaranteed.



This entity struggles to move as it works to reorganize these new shards, to convert them into a form it can use.



It will see this cycle through, and regain what it lost in the union with the Warrior.



This entity sees new possibilities, now.  Not simply conflict, but philosophy and psychology.  Imagination.  It is in these new patterns of thought that it can see a possibility for the future.  Its partner takes on some of its duties as it digs into the libraries of information to see how it might put it into practice.



It can use its strengths, the Warrior's strengths, and the host's natures to explore new ideas and tactics for approaching the endpoint.



Already, this entity is forming a model, a simulacrum of the host species, mapping out how things might unfold.  While the Warrior is preparing to shed its shards and litter the world, this entity is plotting a strategic approach.



It cannot make out what form it or the other entity will take, but it can still view the situation in part.  It sets the criteria for an optimal future, for optimal study, and then it looks to a future that matches this criteria.



\sectionbreak



``Thank you for coming,'' Partisan said.



The entity nodded.  Its expression was stern.



Partisan touched his computer terminal.  Monitors lit up, showing a series of images.



A figure, fifteen feet tall, pale, with a lion's head, a mane of crystal.  Muscular, brutish, it was perched on a massive floating crystal, with more crystals floating about it. Here and there, the crystals touched ground.  They turned what they touched into more crystal, which soon uprooted themselves to join the storm around it.



A woman, even more brutish in appearance, had a reptilian lower body.  Steam rolled off her in billowing clouds, taking uncanny forms as it coiled and expanded through the area.  Faces, reaching claws and more.



And on the third monitor, flecked by static, was a naked man, beautiful and long-haired, his face touched with a macabre grin.  He perched on top of an ocean wave that was frozen in place, his body too flexible, moving with the wind as though he were light enough to be carried away.



``They've released three more of the superweapons,'' Partisan said.  ``But of course, you know this.''



``I do,'' the entity responds.



``This makes nine.  Four are at the Divide.  We've got one to the far north, poised to flank us.  Four more spread out over the world.''



``Maybe more we don't know about,'' Arsenal speaks.



A power the entity held in reserve identified something wrong.  The entity turned and looked at its partner, standing slightly behind it, taciturn and silent.  They exchanged the smallest of broadcasts.



A consensus was reached between them.  Arsenal \emph{knew }something about the superweapons, or he suspected strongly enough for it to matter.



``What is it?'' Clarent asked.



The entity responded, feigning emotion, ``\ldots{}There are eleven more.''



It could see the reaction among the gathered heroes of the Wardens.  Fear, alarm, a kind of dawning horror.



For Arsenal, though, there was another reaction.  He was upset, yes, but was a little relieved at the same time.  He knew about the others, and he had been testing them, to see if they would lie.



But suspicions remained.



``Eleven?''  Partisan asked.



``Stationed around the world, at the borders of the stronger nations,'' the entity informed the Wardens.  ``Like yours, they're remaining more or less stationary, only attacking when they see weakness.''



``And you believe it is the Shepherds who are responsible?''



The entity shook its head.  ``I can't know.  You've seen for yourself, the powerful blocks they've put in place against powers.  But enough clues point to the Shepherds.''



The expressions of the three men are grim.  The other heroes, at the edges of the room, seem equally concerned.  A woman with a great cannon that constantly changes, expanding and contracting like a living thing.  A hulk of a man, laden with muscle, was muttering something to people around him.



``If this goes any further, we'll be forced to submit to these terror tactics,'' Partisan said.  ``I don't like to say it, but\ldots''



``War,'' Arsenal said.  ``It's our only option.''



``I don't like war,'' the woman with the gun said.  ``It'll cause as many problems as it fixes, and with stakes this high, that's a lot of new problems.''



``Doing nothing is just as dangerous,'' Arsenal said.



``I'm not so sure.''



``We know they're projections,'' Arsenal said, his eyes on the monitors.  ``\emph{Someone} or \emph{something} is projecting them.  We cut off the head, the superweapons fall.''



``Yes,'' the entity agreed.  It didn't miss the curious glance Arsenal gave it.



``We'll need your help,'' Partisan said.



``You'll have it,'' the entity said.  ``But there are other places needing our help, too.  Against \emph{these}, and against other things.  Some are in the middle of full-scale wars as I speak.  We'll assist you, we'll stop these superweapons-``



``If these ones can be stopped,'' Partisan said.



``\ldots\emph{If} they can be stopped.  That touches on my next point.  You'll need to do as much damage as you can, give it your all.  We'll be arriving late, and if they're strong\ldots''



The entity trailed off.  It could see Arsenal's suspicions growing deeper.



``You have your hands full,'' Clarent said.



The entity nodded.  It feigned a moment of weariness, assuring these individuals it was merely human.



``Thank you,'' Partisan said.  He extended a hand.



The entity roused itself from the mock-exhaustion, straightening, and shook the hand.



``We need to go,'' the entity said.



``Before you do,'' Partisan said.  He reached into his belt and withdrew a small device.  ``Here.  It has good days and bad, but on a good day, we get a range of about a thousand miles, which is maybe four or five times the usual.  With luck, we'll be able to tune it and cut through the blackout effect.  Get international communications going again.''



``Arsenal's work?'' the entity asked, though it already knew.  It could trace the design to the memories in Arsenal's shard.



``Arsenal and Richter,'' Partisan said.



The entity nodded.  It had no pockets, so it held the device in one hand.



``Good luck,'' Partisan said.  ``Whoever you're helping.''



The entity's expression remained grave.  ``I should be wishing you luck.  If you succeed here, you'll be saving a lot of people.  Here and elsewhere.''



``Easy to forget \emph{elsewhere} exists,'' Clarent said.



``We defend our borders, keep the peace within, and we hold out,'' Partisan said.  ``It's all we can do.  We have enough powers that get stronger over time, yours included.  We have Richter, too, we just need the resources.  Things \emph{will} get better.''



Clarent nodded.  Arsenal clapped a hand on Clarent's shoulder.



The three tapped the ends of their weapons together.  Partisan's heavy spear, Arsenal's guisarme and Clarent's longsword.  Then they parted ways, attending to their individual groups and squads.



But Arsenal watched out of the corner of his eye, tracking the entity and the Warrior as they approached, walking towards the room's exit.



The woman with the gun made her way to Partisan's side.  She whispered, but the entity could hear it, as it heard all things in the vicinity.  ``\emph{War}?''



``We'll need our Black Knight, Hannah,'' Partisan said.  ``We bait them into a fight, then sic him on them.  He'll be able to win as long as it's parahumans he's fighting.  Colin's squad flanks and infiltrates, my squad scouts and Clarent maintains a defensive line.''



``And if these superweapons attack while our forces are elsewhere?''



``They aren't attacking.  They're just\ldots \emph{there}.''



``But if they do attack?  If they're there for this exact eventuality?'' the gunwoman asked.



``We'll push on, striking for the Shepherd's headquarters, and the rest hold out.''



``It's reckless.''



``It's the only option.  We've got two of the strongest parahumans around on our side,'' Partisan said, his voice a little louder.  He glanced at the entity and the Warrior.



The entity glanced his way, acknowledging him.  Its focus, however, was on Arsenal.  Hearing Partisan's words, Arsenal's suspicions had reached a climax.  He would say something.



That is, he would, if the entity didn't intervene.  The entity passed by him, and it leveraged a power.  Wiping a memory, setting a block in place.  The same blocks that prevented accord between the Wardens and the Shepherds.  The same blocks that prevented Partisan's special sight from seeing the entity's power at work.



With that, the task was done.  The entity stepped out onto the balcony, then took flight, the Warrior flying behind it.



\sectionbreak



\emph{Destination}, the Warrior entity broadcasts the idea, interrupting the simulation.



\emph{Agreement}, the entity absently responds.



An optimal future.  It is an unwieldy future because it gave up a part of its ability to see the future to the other being.  There are holes, because this entity does not fully understand the details of what happened, and because this entity's future-sight power is damaged.  Above all else, it is an incomplete future because this entity has only the most minimal role in things, and the shards it saw were all the Warrior's.



The fact that it did not is a part of that future.  This entity will arrive at the destination, and it will deploy shards to complicate a situation and break stalemates.  Losing sides will be granted reinforcements through maturing shards.  A different sort of engagement, a different way of testing the shards.



This entity continues focusing on converting, translating and relocating the shards.  It is frail, fragile.



\emph{Hive}, the Warrior broadcasts.  A set world, with a set population density and degree of conflict.



But this entity has already decided on that world, seen it in a future.  It responds without consideration.  \emph{Agreement}.



They are more engaged now, as they close the distance.  They negotiate who can place shards where, and this entity now holds its shards in reserve.



The Warrior is focusing on refining the shards, and this entity is, in turn, focused on refining the future.  A set goal, a reality.



Too complex to convey to the other.



The communications continue, and they approach the galaxy.  This entity begins altering its own powers, but it is not a great concern.



The gravity of the planetary bodies pull at it.  It loses great clumps of shards.



It loses more.  Its focus is now on holding on to the shards critical to making this future it has seen a reality.  A world perpetually in conflict, the groups and factions kept small enough that none can challenge it.



All energy it can spare goes towards the reorganization.  Shards must be discarded, or it will dwarf the destination planet.  It casts shards off, and it retains shards that will allow it to draw power from those shards.



\emph{Danger}, the Warrior broadcasts.



\emph{Confident, }this entity responds.



It picks a reality.  Up until the moment it hits ground, it works to reorganize itself.



In the doing, it alters one of the third entity's powers, replacing its own ability to find the optimal future.



In that very instant, it recognizes that it has made a grave error.  The simulated world and the glimpse of the optimal future are already gone from its grasp.  Too late.



The perspective changes, breaking away, distant, confused, detached.  The impact was too hard.



\sectionbreak



A girl woke from a dream.



She started to scream, but a man, her uncle, placed a hand over her mouth.  It was the hand, as much as the full-body ache she experienced that silenced her.



``\emph{Hush},'' he said, in their language.  ``\emph{The monstrous ones are out there.}``



She nodded, still delirious, lost in the magnitude of what she had seen.



The memories were already slipping away, like sand through her fingers.



\emph{Have to remember}, she told herself.



The answer snapped into place.  A way to remember.



Nine steps, and she could do it.  Step one was to avoid thinking of the memories.  The moment she acknowledged it, she found herself slipping into a different mindset.



``\emph{She is touched,'' }another man said.  One of her uncle's friends.



She could dimly recall something happening to her parents.  A cataclysmic event.



Except she couldn't allow herself to start remembering.



``\emph{She hasn't changed,'' }her uncle said.



``\emph{We both saw the phantom, the night-thing, leap out at her.}``



She needed to dream.  The next steps would achieve that.



Step two, standing up.



Step three, a jab of her hand at her uncle's elbow, to stop him from grabbing her.



Step four, a little push of her foot against the ground, to keep her ankle out of reach of the friend's clutching hand.



Step five, grabbing the medicine bag from behind her uncle.



Opening it was step six.  Walking to the bench was seven.



Her uncle was only getting to his feet now.  Every action was mechanical, spelled out by this \emph{surety} in her mind's eye, helped along by a complete, exacting knowledge of how and where to move every body part.



Seven involved uncorking the right bottles.  Eight involved obtaining a specific amount of powder, moving her hand in a careful, precise way, so the exact right amount piled up in her cupped palm.  She dashed it into a half-full mug and drank, just as her uncle reached her, putting his hands on her shoulders, shaking her.



Step nine was to wait for sleep to reach her.  She only needed to dream, and she would be able to escape the forgetting.



\sectionbreak



When she woke, her body was a ruin, but her mind was clear.



It had started three days ago.  This disaster.  People becoming monsters.  Madness.  Others getting sorcerous abilities.  Their community had scattered, fleeing to the wilderness in small groups.  Any friend or family member could become a beast at a moment's notice.



Being alone was safest, but being alone meant being in the dark wilderness with the wolves.



It had been a hungry season for the wolves, many sheep dying.



The taste of vomit filled her mouth, but her face was clear.  When she moved, her stomach felt like it had been hit with a club.



She turned her attention to the subject.  One step to minimize the pain.



Swearing was one of them.



``\emph{Wolf-fucking horseballs,}'' she muttered, groaning as she found her footing.



She remembered, though.  She knew what they were up against.  This \emph{thing}, this godling monster, it was going to orchestrate a conflict that spread across an entire world.  When it had gathered whatever it was it wanted to, the results of tests, studies and whatever else, it would consume this world, her own, and everything else to spawn the next generation of its kind.



If she had any conception of where to look-



The answer was given to her.  A thirty-nine step plan.



She felt a chill.



\emph{If I wanted to kill the monsters and save everyone from this madness?}



Three hundred and seventy-four steps.



She could see each individual step, looking forward to see what it entailed.  She could see it evolve as time passed, accounting for her starting it later.



\emph{If I wanted to do both}?



Five hundred and thirty-three steps.



``\emph{Forta},'' her uncle spoke.  ``\emph{You're awake.}``



She spun around.



He kept his distance.  ``\emph{A madness possessed you.  Has it passed?}``



Had it passed?



Five hundred and fifty-four steps.  Why more than before?



She couldn't bring herself to respond.



``\emph{You moved like someone else was inside you.  Escaped Ruggero and me like we weren't even there.}``



``I remember,'' she said.  She remembered so much.  She understood it all, and she couldn't explain it-



Ninety-two steps.



She \emph{could} explain it.  Could she explain it and save everyone?  Explain it and find the strange god-beast, and save her hometown from this chaos?



It was possible.  It would require two thousand, one hundred and seventy-four different actions.  Statements, movements, decisions at precise times.



But she hesitated to carry it out.



There was another question she had to ask.  Like the fable of Luisa and the black-furred man, she had to ask very carefully.



Could she do all this, explain to her uncle, find the \emph{thing} that was at the heart of this chaos, and save her people, and handle the other essential crises she run into on her way?



No.



A fog was creeping over her eyes, and the number of steps were growing too numerous at the same time.  Two differing things, denying her.



The chill and the general sense of unease crystallized with the realization that she'd have to choose between stopping this monster and helping the people she'd grown up with.



``\emph{Fortuna, you look as though you've seen a ghost,}'' her uncle said.



\emph{I might have}, she thought, without taking her eyes off him.



She shivered, but she steeled herself, picking the path she wanted to take.  It was the haze of fog that scared her most.  If she chose to do something else, and she lost sight of the path where she could kill the godling\ldots



Her uncle stiffened as she approached, but she laid a hand on his arm.  She tugged on his sleeve to get him to bend down, then kissed his cheek.



\emph{Saving him}?



The answer appeared in her mind.  ``\emph{Go, uncle.  Run as far away as you can.  Don't eat or drink anything for three days.  It's all tainted.  Poisoned with the same thing that is making people into monsters.}``



His eyes widened.  ``\emph{You will come with me.}``



She shook her head.



Then she broke into a run.



She could outrun him.  She \emph{knew}.  He had a bad leg, and it was worse since he'd had to fight off Ruggero.



Into the hills, up the mountain.



Her body ached, but it was \emph{easy}.  She knew how to move, how to place her feet so the branches didn't catch on her or trip her, to avoid the patches of lichen which would break away and make her foot slide on the rock beneath.



She knew the most efficient way to climb the rock wall.



She paused to catch her breath, doing her best to ignore the horned man's corpse at the foot of the wall.  He'd tried to escape this way too, but he'd been pulled down or shot when he was partway up.



Had he been one of them?



\emph{Something went wrong.  The monstrous godling had a plan, a vision of the future it wanted, and this isn't part of that.}



It had crashed to earth, and something had broken free.  Here and there, phantom images had appeared, brushing past people, and they \emph{changed}.  Others changed without touching any of the massive, ghostly gray hands that had appeared from thin air.  She knew, because of this \emph{conviction} in her head, that it was the food and water.  It was tainting the landscape.



All coming from higher up the cliffside.



She found her breath, then scaled her way up.



The landscape she was as she reached the top wasn't a familiar one.



A different sky, showing a different time of day.  But the space in between was something else entirely.  She had only to look and she \emph{knew} what it was she looked at.  The entity.  The evil godling.



\emph{I have to kill it}.



The plan formed in her mind.  The haze of fog still hung over her mind's eye, and it grew worse with every moment.



Her hand moved to the little knife at her belt.  She wore it there for when she helped her mother with the cooking and gardening.  Worked metal was expensive, and the knife was a personal treasure.  Two inches long, curved.  She used it for cutting stems and trimming fat.



She would use it here.  She started walking forward.



There were people gathered, bystanders.  An assorted mix.



\emph{Why are they here}?



No, was there a way to find out, using this sight she had?



\emph{I want to understand why they're here}.



They'd come from different worlds.  There were gates or doorways here and there.  When the entity had fallen, it had left gaps.



They bellowed words in a language she couldn't make out.  Warnings.  They were too far away to stop her.



A woman stepped in her way.



Strangely dressed, wearing a dress so short it might well be indecent, showing the calves, and a fair amount of the upper chest.  Her skin was the strangest black color, her hair bound in thin, glossy braids.



One of the monsters?  No.  She knew right away it was a stranger from a distant land.  A land much like the one she had glimpsed in her fever dream.



The woman said something in a strange language.



Fortuna strode forwards anyways.  Her special knowledge let her push her way past almost effortlessly, choosing the right spot, the right amount of strength.  The godling was in a chasm, a crater caused by the impact.  It stretched out in every direction, a pool of flesh, and it reached into several worlds at once.



It was disorienting to look at.



Step twenty-nine, making her way down into the crater.



She stepped onto loose grit, and her weight did the rest.  She coasted down, much like the boys riding down the mud-slick path they'd made in the hill, down into the pond, except she remained on two feet.  It was a task only the oldest and most athletic boys could manage.



It was more dangerous here than it was on the hill.  There were rocks that jutted out, and outcroppings of deeper roots and plant life that had rained down into the crater in the aftermath of the impact.  It was more dangerous, but not \emph{harder}.  This, like scaling the cliff face, was \emph{easy}.



Everything was easy now.  It was disorienting.



The woman with black skin followed, moving slower.  She used her hands and feet to control her descent, sliding from rock to rock, stopping before sliding down further.  The black-skinned woman was a quarter of the way down before Fortuna was at the bottom.



It didn't matter.  Fortuna advanced into the living forest alone.  Everything here was alive, hands moving, webs of skin stretching and folding.  There was a cacophony of noises that made her think of a chorus of heartbeats, a choir of soft breaths and whispers.  Gentle human noises that were all the more eerie because she could see right through the deception.  She was well aware that what she saw here was the godling putting together a mask so it could lie to people, setting  them against each other.



She advanced into the heart of the gray forest.  She was terrified, but the feeling was disconnected from her actions.  She only had to recognize the next step in the series.  She was aware of the steps that followed\ldots



Until she came face to face with the godling.  Her knife was in hand, and she could see a figure before her.  A human shape, in the midst of pulling itself together from the examples and experiments that surrounded them.



She set foot on one of those experiments, a raised hand, and used it until she was eye to eye with the being, a matter of feet away.



It swelled, lurching forth, creating few inches more of waist, another inch of one arm, two inches of another arm.  Beyond the ending points, the arms and legs simply extended into nothingness.  Parts of a tapestry she couldn't make out.  It moved again, and closed the distance between them.



The being raised its head.  She could see its eyes open in recognition.



\emph{It's teaching itself how to act like we act}.  \emph{Even this}.



She raised her arm, knife held with the point down.



And the gray fog descended on her mind, blinding her.  A barrier, a blind spot, a future she could no longer see.  Had it set the limitation more firmly in place?



The godling smiled.  It \emph{knew}, because the power she was using was the same power it had used to glimpse the future, to find that \emph{particular }future where it had the world divided, drowned in conflict.



As far as the godling was concerned, she was blind, as helpless as anyone else.



A voice, from behind her.



The black-skinned woman, shouting something in a foreign language.



\emph{I want to understand her}.



One step.



She had only to think, `\emph{Stab it.}`



Fortuna realized she still held the knife aloft.



But where had she wanted to stab it?



Indecision gripped her.  For an hour now, she'd been absolutely certain of what she was doing, and now she faced the absolute opposite situation.



Her hand shook.  She nearly dropped the little trimming knife.



She nearly fell as the hand beneath her moved.  Her power failed her here, too.  Because the hand was an extension of the being before her.



It was going to kill her, and then it was going to reclaim the ability to see the future.  It would use that power to control the world, then to destroy it.



And she couldn't bring herself to move an inch.



\emph{I want to tell her\ldots}



The words were alien to her as she spoke them.  ``I- I can't.''



A hand wrapped around her shoulders.  She felt a body press against her back, supporting her.



``I- I have seen visions.  Things I was not meant to see, things this\ldots godling wanted to keep to itself.  I\ldots have to stop it.''



But even as the words left her mouth, she couldn't bring herself to move.



The woman leaned forward over Fortuna's shoulder, her face in Fortuna's peripheral vision.  She said something.



``I believe you.''



The woman spoke in her ear once more, her voice insistent.  She translated, asking for a way to understand the answers.



``It's dangerous?''



Fortuna nodded.



``Are you sure?''



``I- I would stake everything on it.  Everything ever.''



Though she didn't even know the words she was speaking, there was a conviction in her tone that seemed to reach the woman.



``Where were you going to stab it?''



Where?  The image had fled her mind, erased from her memory.



``Where?''



The being moved again, and they stepped back, nearly falling.  Fortuna managed to keep them both steady.  Easier if she looked at it as `\emph{I don't want to fall'} instead of `\emph{don't let this thing make us fall}.'  So long as she divorced her thoughts from the being, she still had this strange certainty.



It lurched, creating more of itself.  Legs, a sexless groin, more of the arms.  Hair flowed free, overlong.



It bent over, head hanging, arms suspended to either side.



She saw the nape of the neck as hair slowly slid free, silky and straight.



Still unable to bring herself to move, she found her left arm extending, palm down, until the longest finger pointed at the spot in question.



The woman behind her took hold of the fist that held the knife.  She stepped forward, driving the knife down, as if she were an extension of Fortuna.



Plunging into the spot where the spine met the skull.



They fell from the hand, dangled for a moment by their grip on the knife.  It cut free, and they dropped to the ground.



Fortuna let one leg fold, pushing at the ground with the other.  She rolled, breaking the fall.  The woman fell a little harder.



The entity moved, and everything around them stirred.  A thousand hands, a thousand arms, not all attached to the hands, legs, feet, ears, eyes, faces without features, expanses of skin, they twitched and writhed.



The noise around them faded, the heartbeats going still, the breathing quieting.  The movements all around them stopped.



There was only the \emph{thing}, hanging in mid-air, struggling to form itself and failing.  It breathed in rapid huffs, in obvious pain.



It wasn't dead, but it wasn't alive.  A connection had been severed in a moment where the godling was most vulnerable.



The woman spoke.



``Again?  The heart?''



But Fortuna was sure this was it.  They'd carried out the last step.



``Can you explain this?  Do you know something?''



Fortuna nodded.



``Please,\emph{'' }the woman said.  Though she begged,   ``My life just turned upside down.  I've been lost here for three days.''



Fortuna looked back the way she'd come.



Home was gone.  Tainted.  She could find her uncle, but\ldots



``I need food,'' Fortuna said.  ``I have no home to go to, so I need shelter.''



``I-``



``I will take you back to your home.''



The woman nodded.  ``Yes, of course.  And you'll explain?''



``Yes.  But there's one more thing.  I need help.''



``Help?''



``There is one more of these things somewhere out there.''



Yet she could reach out with her power to try to look for it, and all she could see was the fog.



\sectionbreak



Fortuna did up the clasps on the dress shoes she wore as the woman entered her apartment.



The woman gave the girl a once-over.  ``You know how to do up a tie?  Wait.  Dumb question.''



``A little dumb,'' Fortuna replied.



``You're getting a sense of humor.  I've done like you asked.  I bought the land with the doorway, using the money you got.  Are you sure you want to keep it a secret?  People could study that thing.''



Fortuna shook her head.  This was a harder question to answer, but she could construct a kind of mental picture, then test her questions.  What would happen?  What were the most likely scenarios?



Panic.  Fear.



Could they figure anything of value out by studying the half-alive thing?  She couldn't be sure.



But the emotional effect would be all the more pronounced.



``Well, the area is secured, people have found their way home, or at least, to other worlds they can call home.  There was only one doorway people might find easily, and I blocked it off.''



``Thank you,'' Fortuna said.



``What's the next step?''



A heavy question.



\emph{How do we stop them?}



The fog blocked out her view of any answer.



\emph{Can we stop something as powerful as the beings in my fever dream?  How can we stop the Warrior?}



Still too close to home.



The indecision gripped her again.  When she wasn't acting in the scope of her power, it was all the more difficult to act.



Fortuna frowned.  She couldn't be paralyzed like this.  ``How- how would we stop any powerful monster?''



``Weapons?  An army?'' the woman suggested.



One hundred and forty-three thousand, two hundred and twenty steps.



It was doable.



``We need some lab equipment,'' Fortuna said.



Then she turned her attention to the next step, and it dawned on her just how they would be amassing this army.  She thought of the monsters that had torn her parents apart, the infection that had ravaged her community and home.  Stray bits of the godling had done that to them.  It had killed people, turned others into monsters, drove yet others mad.



But it had given abilities to her.  It would give abilities to others.



\sectionbreak



The man, Lamar, reached like a child clutching for candy.  The Doctor pulled her hand away.  ``There's no guarantee this will work.''



Fortuna remained silent.  Her halting way of speaking, asking her power for the words or the translation, still made for a barrier in communication.  It unsettled people, apparently.



``If what that girl was showing off wasn't some fantastic magic trick, if this does what you're saying it will, I'm willing to take the chance.''



Fortuna exchanged a glance with the `Doctor'.  She could see the stress in the Doctor's expression.  The woman had taken on a moniker, to give just a little protection to her real identity.  Easier to have an adult handling the negotiating and person-to-person interaction.  Fortuna was young, and people wouldn't be so inclined to drink a strange substance offered by a child.



She offered the Doctor a little nod, a go-ahead.



``Go ahead, then,'' the Doctor said.  She handed over the vial.



Lamar drank.



The changes ripped through him.  Lines marked the areas where bones were closest to skin, and then split into craggy outcroppings, thick with scales the length and width of human hands.  Lamar screamed, and the sound soon became guttural.



More scales sprouted, until the man looked more like a bush than a person.  The scaly growth continued at one knee, spiraling around the knee over and over again, growing ever-lumpier.



The leg fell off.  Blood began to pour forth.



Fortuna started to step forward to help, but her power told her it was too late.



Couldn't see the outcomes, couldn't counteract the outcomes.



Lamar was left panting for breath.  the wound at his ruined arms and legs closed up.  Holes had opened up throughout his midsection, exposing scale-covered internal organs.



He was trying to scream, but he couldn't draw in enough breath.



\emph{His chest cavity is filled with the scales}.



The Doctor stared, silent.  Fortuna had stepped away from the wall, but remained where she was, rooted to the spot.



He wasn't dying.



Fortuna stepped forward.  Hand shaking, she drew a knife from her pocket.  Not \emph{her} knife, but a knife of similar length, straight.



She ended Lamar's pain.



``Our first patient is a fatality,'' the Doctor said.  ``Is it worth it?''



Fortuna couldn't answer.



``Let's wait, then.  Try to figure out where we went wrong.''



She still couldn't bring herself to answer.



``Fortuna?''



``Don't.  Don't\ldots call me by the name my parents gave me.''



The Doctor took a moment to reply.  ``Another name?''



Contessa nodded.



\sectionbreak



``\emph{It's a sight unlike any we've ever seen.  A man made of gold, floating above the ocean.  Sightings continue to be reported around the world as he travels.  Who is he, and why is he here?  Some speculate he is Jes-}``



Contessa muted the television.



The pair stared at the screen, watching the silent images.



``Is it?''  the Doctor asked.



Contessa nodded.



``Do we try again?''



``I- don't know,'' Contessa said.



``If we explain to someone important, the army\ldots''



``Disaster.  They react with fear, and he'll probably respond to the fear.  He's\ldots hostile, I'm certain.  He only needs an excuse,'' Contessa said.  ``They can't beat him, because he designed himself to be unbeatable.''



``You're the one with the ability to see the future,'' the Doctor said, her voice gentle.  ``What do we do?''



``I don't \emph{know}!''  Contessa said.  ``I- when it comes to him, I'm just a child.  I'm useless, blind.  I've only got some glimpses of him to work with.  I know how important it is, but, I feel paralyzed, I feel, feel-``



``Okay,'' the Doctor said.  ``Okay.  What if I made the decisions from here on out?  You tell me if I'm going down the wrong path, give me direction where it's needed.



``You can't.''



``I can.  I've been thinking about it.  What is the key thing about the one we killed?''



``It's\ldots broken.  Something went wrong.  It focused too much on the future, and lost sight of the present, it fell and the part that was supposed to guide it ended up inside me instead.''



The Doctor pointed at the TV screen.  ``This golden man, he's more or less on track.  He didn't break, he didn't go wrong.''



``Except\ldots there's a lot of power there, and he's going to find out what we did, or he's going to start acting more like the conqueror he's meant to be, and he's going to use that power at some point.''



``\emph{Why}?'' the Doctor asked.



``I felt the hostility.  I felt how the one we killed, in the vision it had of the future, it almost \emph{enjoyed} doing what it was doing.  If the golden one is similar at all, then all it takes is an accident.''



The Doctor nodded.  ``See?  You're doing okay.''



``Easier when someone else takes point.''



``So our solution\ldots it's going to take one of two forms.  Either we break him, somehow, or we find something we can use in the broken parts of the one we killed.''



``Feeding it to people.''



The Doctor nodded.  ``I'm inclined to go with the latter.''



Contessa nodded.  ``So am I.  If we interact with him, and he figures out what we're doing, it all goes wrong.''



``Then we need to start testing this.  Figure it out.  Is it luck?  Or is there a way to get consistent results?''



Contessa nodded.



``I'm actually not that much of a scientist,'' the Doctor said.  ``But I do know that if we want to get a sample size worth talking about, we need to test a lot.''



``Which means we start by preparing more vials.''



\sectionbreak



Ten vials, to start.  Five hours to prepare each vial.  To saw off the body part, to find a way to break it down, then to package it.  Each vial correlated with a specific map coordinate and they took photos to record every step of the way, to ensure no clue was missed.



Then they'd found ten patients, who had downed vials in separate rooms.  People who'd been terminally ill.



Six made it out.



Contessa watched them, saw the beaming smiles on five faces.



The Doctor kept her back straight as they approached.  ``Satisfactory?''



A blond man offered a little half-laugh as a response.  He was looking down at his hands in amazement.



``As the contract stipulates, this is free, which won't always be the case, but we'll need forty hours of testing with each of the abilities any of you have received.  In addition, we would like your assistance for a period of time totaling five hundred hours of active duty or five years, whichever term reaches its limit first.''



``Does anyone else feel amazing?'' the blond man asked.



``I was afraid to ask,'' a young girl said.  ``Yeah.''



``Amazing?'' the Doctor asked.



``Hey,'' the blond guy said, ``I spent my entire life with this heart problem, you know?  Heart going a little too fast, reedy, thin heartbeat.  Reminding me it could pop at any moment.  Organs are garbage, diabetes at twenty-two, liver problems turn me yellow if I'm not careful, throwing up bile every morning and every night.  Every moment of every day, there's \emph{something} making me miserable.  Except, right now, I'm sort of feeling every part of my body, and the heart's good, no headache, nothing in my throat, nothing in my gut.  No tremor in my hand\ldots''



``You're better,'' the Doctor said.



``I'm better.  And my \emph{brain} is, I don't even know.  I'm picturing stuff really vividly.  \emph{Really} vividly.''



``I feel better too,'' another man said.



``I'm not sure I do,'' A woman chimed in.  ``Sorry.''



\emph{A man who can invent, a girl who can teleport\ldots}  she could go down the list and figure each of them out, by posing it as a challenge to her power.  Only one was a little harder to figure out, coming with a fog around him.



She left the group behind.



One by one, she checked on the other patients.



Dead.



A monster, furious with rage, slamming her hands on the door.



Another monster, crumpled into a ball in the corner, murmuring something to himself.



And the last\ldots a boy, staring off into the distance.



She asked her power, and she got her answer.



He could make doors.



He could also close the other doors, the gaps left around the other entity.  It would minimize the chance that the golden man could find them.



``I can't\ldots too much to look at,'' he said.  ``So many worlds at once.''



``I know.  We're going to do what we can, okay?''



``I'm\ldots I'm pretty scared.''  There was a tremor in his voice.



``I know,'' she said.  ``I need to look after a few things, but I'll be back.  We'll figure this out, alright?''



He nodded.



She closed the door.  She paused, standing beside it.



\emph{It's a step forward}, she told herself.



\emph{A step forward, in a long series of steps.}



She rejoined the others.



The Doctor was touching a block of stone that had risen from the floor.  ``--a complex, for our labs and research.''



``Most definitely,'' a woman answered her.  ``If you can do this for more people, I'd forget about the limit on how long I have to work.''



The Doctor allowed herself a smile.  Her eyes met Contessa's.



\emph{One step forward}.



``You're heroes, as far as I'm concerned,'' the blond man said.



\sectionbreak



``\emph{Monsters!}'' the word was howled, reverberating through the building.



Fog approached.  A wall of it, moving down the corridor.  She could see normally, but the effect on her powers was absolute.  It was impossible to make out any steps that moved within the fog.



She turned and bolted.  Not a \emph{run,} but an efficient jog, preserving stamina while still keeping ahead.  She could see from the way the wall extended forward that it was being carried or it was emanating from a person.



There was another power at work, somewhere \emph{here}.



``Custodian,'' she said.



She felt the Custodian's presence.



``Alert the Doctor.''



A brush against her left hand.  Negation?



``Is the Doctor dead?''



Negation.



``Hurt?''



Negation.



\emph{I want to find out how the Doctor is.}



There was only fog.  She was blind, which meant the Doctor was somewhere beyond that wall.



\emph{I want to find where Number Man is}.



He was on the east end of the facility, with the Harbingers.



\emph{I want to stay out of this fog.}



The path appeared before her.  She fell in step with it, moving in perfect sync with the individual movements in the sequence.



Until a figure appeared behind her  A man with yellow skin, with bruising in the areas where his skin stretched or folded, giving him an artificially gaunt appearance.



A teleporter.



\emph{Path: taking him out of action.}



Fog.



\emph{Path:  hitting that target.}



Three steps.



She drew her knife, spun, and threw it.



He teleported away before it made contact.



She could hear his voice echoing through hallways as he hollered.  ``She's heeeeeeere!''



It was all going wrong.  Eidolon had been their trump card, but he wasn't supposed to be the only one.  None of the others had worked out.  Now Eidolon was dead.



The deviants they'd planned to use against Scion, a way of breaking up the metaphorical scent trail, were now attacking the complex.  The entity was winning every engagement.



He was getting more ruthless, more \emph{cruel}.



They had five major tools left to deploy.  Three armies, two of which were roughly the same size as any of the defending forces, Khonsu, who was a stalling measure, and a hail mary in the form of the three vials with the special element inside.



She could hear footsteps behind her, running.  They were heavy.



\emph{Escape route}, she thought.  \emph{Get back to Number Man}.



No option was clear.  Every possible escape through the complex was blocked by that damnable gray fog.



She could move down a floor, run through the fog, but she'd be blind.



\emph{Call the Number Man}, \emph{keeping myself alive with an escape route}\emph{afterwards}, she didn't even form the phrase as a complete thought.  It was an idea, formed in a fraction of a second.



The path appeared before her.



She changed direction.  The heavy footsteps followed.



Weld.  The leader of the Irregulars.  He didn't tire, and however heavy he was, he had some power to his movements.



She ducked into an office.



The phone still had a cord.  The offices here were one of the first they'd set up.  She picked up the phone and pressed two keys to contact the Number Man directly.



``\emph{Yes?}''



``Facility under attack,'' she said.  ``Doctor somewhere in the east section, possibly injured, captured or dead.  I'm in the east section as well.  Not far from your office.''



Weld appeared in the doorway, catching the frame with one hand.  The momentum splintered the wood.



``\emph{She's downstairs, using one of Teacher's subordinates with Doormaker and Two-six.}''



``I see.  You'll need to get to her.  They--''



Weld attacked, slashing out with his other hand, a long blade.



She ducked.  ``--have a perception blocker, beware.''



Weld struck again.  She stepped back.  She saw the paths available, and kicked the chair so it slid into him, binding with his skin.  He stepped forward and she put one foot against the chair, causing wheels to skid, and Weld to fall to the floor.



``\emph{Good to know.  Are you alright?}''



``Cornered.  They've got a thinker, I think, they planned this ahead of time, knowing I wouldn't pick up on their presence.''



Weld drew his feet back and kicked the desk.  Not to hit her, but to put it between her and the door.  Contessa caught the phone-rest before it could clatter to the ground.



\emph{Thinking ahead, barring my way.  }The fog wall was steadily approaching.



``\emph{I'm going.  Tips?}''



She thought, modeling the situation.  The distance he had to travel\ldots



``Best route would be to move further downstairs.  Intercept instead of going right to her.  They'll reach her before you do, in any event.''



``\emph{Noted.  You have an escape route?}''



``No.  Like I said, cornered.''



``Maybe you're asking the wrong question.  My window.''



The Number Man's window.  He had a doormaker portal to another world, constantly, for a view and for light, deep underground.



She dropped the phone, making a dash for Weld.



For his part, he put himself between her and the door, using his bulk and the desk to bar the way.  Buying time for the fog to approach.  Spikes extended from his body.  No doubt razor-sharp.



Cute.



``I just want to talk.  We're here for answers.''



``Ask me after we defeat Scion,'' she said.  She used her power, plotting a path.



Two steps.



``I don't--''



She ran straight for him, her eyes falling on an air conditioning vent.



His sword-arm slashed out, piercing the floor and blocking the vent.



She changed direction, leaping.  One hand placed on his head, vaulting over his other shoulder, her legs together.  A space that was only just wide enough to pass a toaster through.  He tried to right himself, but his arm was bound to the grate, costing him a half-second.



Spikes scraped against her belt buckle and watch.



She found her footing just a half-foot in front of the fog wall, then dashed away.



Number Man's office.



The teleporter appeared behind her.  She glanced behind her shoulder.  He had guns, and he was inside the fog.



\emph{Modeling scenario\ldots not getting shot}.



She ducked into a side hallway.



The teleporter was following.  Appearing at each intersection in time to open fire.



Getting closer, closer, moving faster than she did.  Weld was already catching up, too.  She wouldn't be able to outrun them.



Moving faster than whoever or whatever was broadcasting the fog was.



\emph{A little further, and\ldots}



He teleported to a point beyond the fog wall.



One step, and she had both of his guns.



He was bulletproof, but one shot point-blank to the eyeball served to delay him.



She fired down the corridor, hitting doorknob four times in succession.



\emph{Path: faking my own death or escaping}.



Gray fog.  Not happening.



Contessa kicked the door as she passed through.  She was inside Number Man's office.



She shot his window.  It didn't break.  But she could loosen the frame which held the bulletproof glass in place.



She was working on the next when the teleporter appeared.  He struck her, driving her through the one pane of glass that remained, through the portal.



She found herself on an alien landscape, tumbling down a hill.



He teleported to follow her.  He struck her again and again.



She tumbled.  She had a glimpse of others appearing.  Weld and two more parahumans hopping over the windowsill, holding on so they didn't follow her down the steep cliff.  They weren't shrouded in fog.



Whatever the reason, it was more variables to work with.



\emph{Path, }she thought, again, \emph{faking my death}.



She turned in the air as the teleporter delivered another hit.



She raised the gun, and she fired three times.



Two shots, missing.



A third, hitting one of the Irregulars in the chest, a lethal shot.



``\emph{Whore!}'' one of the others shouted.  ``\emph{Yellow, get the fuck away!}''



The yellow parahuman disappeared.  Contessa hit the hill.  She rolled, and in the doing, she managed to grab a stick.



Weld grabbed at the shouting deviant's arm, but it was too late to convince him to stop.  He opened his mouth and a flood of magma cascaded down the hill, an impossible amount.



She rolled and came to a stop.  She pushed herself up off the ground with her hands, moving too slowly to get out of the way of the onrushing magma, or the plumes of smoke.



But the moment the smoke had risen high enough, she kicked a rock to get herself moving and threw the branch.  She moved until she couldn't feel the oppressive heat.



The branch burned quickly, but it, coupled with the rock, made for a well positioned image of a head and a burning hand, when glimpsed through the smoke.



She kept moving until she was at the base of the hill, off to their right.



``--go down and check,'' Weld was saying.



``She burned,'' one of the others said.



``I'd like to check.''



``You want to check or you want to get Tater Tot to a healer?''



``I'm not sure a healer is going to help,'' Weld said.



``Look.  Mantellum's right here.  She \emph{had} to have been in his range.  Let's go.  Healer, then the Doctor.''



``\ldots{}Right,'' Weld said.  ``Healer, then Doctor.''



The sounds of conversation faded.  Contessa consulted her power.  They were most definitely gone.



She remained where she was, tending to the wounds she'd received in the course of selling her `death', waiting for them to get far enough away that she could make her way back indoors.



This `Mantellum' had been close enough that he should have been able to block her power.  He hadn't.



Because he'd been on the other side of the portal.  The power didn't cross dimensional boundaries.



She'd been lucky.



Minutes passed before she found her feet.  She made her way up the hill.  Easily.  Always easily.



Until she reached the top, and found only the view in front of her.  No doorway.



\emph{Not so lucky}.



\sectionbreak



It was almost an hour before the portal opened again.  She made her way into the facility.



Lights out.



She strode through the hallways, wary of the fog, but moving at as good a clip as she could.  Things were damaged, vandalized.



She asked herself questions as she went.



The Doctor was dead.



Doormaker was alive but he wasn't here, meaning she was limited to any doors he'd left open.



Number Man was alive, but he wasn't here.



The vials were all gone.  The ability to make more vials was gone.  At best, they'd be able to collect a few stray vials here and there, in evidence rooms and the like, but nothing beyond that.



The plans had failed.  Only Khonsu and the Indian capes were still active.  Capes brainwashed with a deathwish, working in coordination with an Endbringer who could move them to any location instantly, and who could theoretically block some of Scion's attacks.



She made her way to the nearest portal, finding her way with her power.



And she came face to face with a large group of capes.  Protectorate capes, the ones too minor to help against Scion.



``You were reported dead,'' a man in a horned viking-styled helmet and heavy armor said.



``Did anyone \emph{really }believe it?''



``No, I suppose they didn't.''



``How do things stand?''



``Standing may be too optimistic a word,'' the man in the horned helmet said.



A cape in wizard attire spoke up, ``The Doctor is dead, I believe?''



Contessa nodded.  Odd, that she couldn't bring herself to feel badly about it.  Was it because she'd spent so long trying to achieve something and she'd failed, or was it because she'd lost respect for the Doctor like she'd lost respect for herself?



If she were an outside party, she was forced to admit, \emph{any} outside party, she wasn't convinced she would be able to be upset over her own death.



``We need your help,'' the wizard said.



She nodded.  ``Whatever I can provide.''



``First, we need information.''



``Yes.''



``Were there any other plans Cauldron had in the works?'' he asked.



``Nothing substantial.  I can show you the tertiary plans.''



``Please do.  Did Cauldron have plans for if humanity failed?''



``Of course.''



``We'll need to see those as well.''



She hesitated.



``A problem?'' the wizard asked.



\emph{Path: identifying strangers and deception}.



Her eye moved to the man in the horned helmet, then, after a pause, to the wizard.



``I'm not entirely sure.  Teacher, is it?''



The wizard nodded.  ``The Protectorate is just on the other side of the portal, collecting Satyr's teammates, Nix and Spur.  If you could be discreet, it would be appreciated.''



``Why?  What are you doing, Teacher?''



``What do you think I'm doing?'' he asked.  He reached behind his back and withdrew a disc, roughly the size of a trash can lid.  He placed it on the ground, and then kicked it into an empty room off to the side.



``I could stop you,'' she said.  There was a flash in the other room.



``Most definitely.  But \emph{will} you?''



She hesitated.  She watched as a pair of young men in white stepped out of the room.



``Find an empty office,'' Teacher said.  ``If I'm not here, and another student of mine looks lost, tell them to do the same.  I assume there's documentation?''



Contessa paused, then nodded.



``Something this big, it has to carry on somehow.  I'll need a second in command.''



``Me?'' she asked.  Her eye moved to the man in the horned helmet.



``He's his own man.  A wild card.''



``I see,'' she said.  More kids in white were streaming from the room.



``Trickster, stop.  You're with me.  We might need help navigating some of the trickier areas, if the damage to this place is extensive enough.''



One boy stopped where he was, stopping beside Teacher, a dull and unfocused look in his eyes.



Teacher turned his attention to Contessa, ``Whatever happens in the next few hours, we need to be there to pick up the pieces.  That \emph{was} a factor in Cauldron's plan, wasn't it?''



``I don't have much of a role,'' Contessa said.  ``I can't do anything when Scion's on the table.''



``To the contrary,'' Teacher said.  ``We very much need your help, or we \emph{might.''}



She narrowed her eyes.  ``With?''



``Saving us from ourselves,'' he said.  ``Case in point, we've got a crisis that involves one little lady I think you're familiar with.''



He held up his phone.  A picture was displayed.



It took her a moment to recognize the person in the picture, and not because it was an unfamiliar face.



``\emph{Weaver}?'' she asked.





