





Couldn't catch up, not with the Undersiders mounted and us on foot.  I could fly, but I couldn't abandon this team.  If Tecton hadn't deferred leadership to me, I might have taken on a scouting role, flying ahead, notifying the Undersiders.



This was the worst environment for me.  There were bugs aplenty, but the area was thick with smoke, and there were fires everywhere.



Bugs weren't going to contribute much.  They were getting roasted, by hot air and scorching smoke if not the fires themselves..



I flew from point to point.  Navigation wasn't my strong point, so I focused on moving in straight lines, stopping at various vantage points where I was fairly confident I was out of Behemoth's sight, physically reorienting myself, then flying to another point.



Each time I stopped, I took a second to try to grasp the situation.  The streets were flooded with people, and it was only getting worse.  The troops we had on the ground were struggling to make headway, and from my vantage point, I could tell that things were getting worse.



The approach had an added advantage in that it let me track where the fires were.  I collected bugs, took a moment here and there to analyze them, assess their capabilities, and guided them along my general route, keeping them as safe as I could manage.



There was a crash as a building toppled, sparks spilling out into the air.  I could hear screams, distant, as the crowd recoiled.  Through the bugs in their midst, I could sense the way they were scrambling for cover, for safety.  The nearest path that took them away from Behemoth was towards \emph{us}.



Rickshaws turned around and made their way for the mouth of the narrow street, people pushed and shoved, and otherwise \emph{stampeded} towards us.



I was in the clear, but my team\ldots  I flew a short distance away to check everything was clear, then started to make my way back, still flying in short bursts.



\emph{Flitting here and there, }I thought.



\emph{No,} I thought, banishing the idea from my head.  \emph{Not flitting.  Never let that word slip in conversation.  Makes me think of fairies.  It'll make Glenn think of fairies}.



``Tecton!'' I called out, as I returned to my roost.



He looked up at me.  Even with his heavy body armor, he was struggling with the mass of people who were pushing and squeezing their way past him.



I pointed, ``Go through the building!  ASAP!''



He looked at the building, then raised his gauntlets.  The piledrivers slammed into the wall, punching out a rough, door-shaped hole.



He strode through, then did the same for another exterior wall.  The Chicago Wards flowed through.



``Not used to being allowed to make messes,'' he said, his voice loud.  ``This is just about the second time I can go all out!''



``Powers,'' I said, flying down to ground level.  The smoke wasn't as bad down here.  ``You've had a few minutes to think, rookies, give me a quick rundown.''



``To \emph{think}?'' Cuff asked me.  ``The hell?  You can \emph{think} with all this going on?''



``You're clear of the crowd,'' I said.  The number of people here were only half that on the other street.  It was a herd mentality, \emph{lemming} mentality.  They were too focused on getting away.



``It's not just the crowd.  It's-'' she flinched as lightning struck somewhere in the distance.  ``We could die any second, just like \emph{that}.''



She was showing it the most, but I could see the fear in the other two, as well.  In \emph{everyone}, but these guys in particular.



\emph{They're new.  They've probably never been in a real life or death fight}, \emph{let alone something like this}.



\emph{Hell, I've never been in a fight quite like this.}



It was ominous, the fact that the armbands were silent.  The A.I. wasn't counting off a death toll, and I doubted it was because nobody with an armband was dying.  Maybe Chevalier had made a call, deciding that morale was low enough without an artificial voice reading out the names of the dead.



The only noises were the impacts and rumbles of Behemoth's fighting against defending capes, the screaming and panting of people who ran past us, and the incessant crackle of nearby fires and crashes of thunder.



``We stand better odds if you pull yourselves together, fill us in, so we can use each other's abilities to help,'' I said.  ``Come on guys, work with me.''



``I'm a breaker and shaker,'' Annex told me, ``Merge into nonliving material, warp space.''



``Warp it how?'' I asked.



``Reshape it,'' he said.  He was still half-walking, half-jogging, but he stretched a white-gloved hand out four feet, touching a sign.  His hand smeared against it as though it were more liquid than solid, coloring it the same white as his glove.  The sign oozed back into the wall, virtually disappearing, and Annex removed his hand, slowly reeling in the extended flesh.  The sign remained where it was, compressed against the wall, the surface flat.



``Okay,'' I said, making a mental note.    ``Okay, good.''



``While in there, I'm about as tough as whatever it is I'm controlling,'' he added.



``Alright.  Golem?''



Golem had to stop running to demonstrate.  He dropped to one knee and plunged a hand into the street.



Ahead of us, there was a crash, a grinding noise.  A hand made of pavement was reaching out of the ground, five feet long from the base of the wrist to the tip of the middle finger.  The fingers seemed to move in slow motion as the hand pushed against stopped cars that were sort of in our way, shoving them to one side of the road.



The hand submerged back into the road as he withdrew his own hand from the street.



``Okay,'' I said.  \emph{There's synergy with Annex.  Maybe Tecton too}.  ``Anything I need to know?  Limitations?''



``Whatever I use my hand on, has to match the exit point, pretty much.  Asphalt for asphalt, metal for metal, wood for wood.''



I nodded.



``Bigger the thing I'm making, slower it comes out, slower it moves when I try to use my fingers.''



``Anything else?''



``Lots more, but mainly I can only use my hands, arms, feet and legs.  My face, but that's not too useful.''



Cuff made a small noise as something crashed in the distance.



``Cuff?'' I asked.  She didn't reply.



``Cuff!'' Tecton raised his voice.  It seemed to wake her up.



``What?'' she asked.



``Your powers.  Explain.''



She shook her head, ``Um.  The, uh-''



When she didn't pull herself together enough to reply, Tecton set a heavily armored hand on her shoulder, ``She's a metallokinetic.  Shape and move metal, short-range, including the stuff she's wearing.  Some enhanced strength and durability, too.''



``Yeah,'' Cuff said, her voice quiet.  ``Not half as cool as those guys.''



``It's good,'' I said.  I noted how she'd paired up with Grace.  Did Cuff's presence have anything to do with the fact that Grace was wearing PRT-issue chainmail?  They didn't give me the vibe that they were a\emph{ pair }in any friendship or romantic sense, but they were two bruisers, two girls in a group of mostly boys, and they were sticking together.  That seemed to be enough.



I was going to say something more, but a crash and the rumble of something falling down nearby stalled that train of thoughts.



``Oh fuck,'' Cuff said under her breath, as lightning struck close by.  She was panting, and I suspected it wasn't the exertion.   ``Oh hell.  Why did I wear a costume made of metal?  I'm a walking lightning rod.''



``You've got a regulation suit between the metal and your skin, right?'' Tecton asked.  ``If it's a type three or type four-''



``No suit,'' Cuff said.  She tapped the metal at her collarbone, ``Strongest if metal's in direct contact with my skin.  Got a layer that's almost liquid between this and \emph{me}.''



``You didn't think to change?'' he asked.



``I didn't think,'' she said, her voice quiet, harboring a tremor.



\emph{Why the hell did she come, if she was going to be like this}?



``Fuck,'' Wanton said, ``You \emph{are} a lightning rod.''



``I don't think you're any safer or worse off than anyone else,'' I said, trying to inject a note of confidence into the discussion.  I raised myself a step off the ground to get a better view of what lay ahead.  The ground was shaking, a steady, perpetual tremor.  ``His lightning doesn't follow regular channels.  We're \emph{all} lightning rods to him.''



Cuff didn't respond.  I glanced down to see her frowning.



``\emph{Not} reassuring,'' Wanton said.



``It's the truth,'' I said.  ``We accept it, take it in stride and \emph{use} it.  Can we change that fact?  Or use it to our benefit?''



``He'll zap us to death with one hit, even if we protect ourselves,'' Wanton said.  ``Yeah.  There's a benefit there.''



\emph{These guys aren't the Undersiders.  Different strengths, different weaknesses}.  The Undersiders were good at approaching things from an oblique angle, at catching people off guard, being reckless, even borderline fatalistic.  They had been more experienced than I was when I joined.  It was the other way around here.  Even Tecton, the oldest member of the group, the official leader, had less experience than I did.



I didn't know them well enough to be able to guess what they brought to the fight.  I considered the various powers as I flew from point to point, scouting with eyes and careful use of my swarm.  Didn't want to let any of the mobile ones get burned up.



The swarm included fruit flies, mosquitoes, cockroaches and house flies, identical or almost identical to the ones back home.  Surprising.  There were some smaller varieties of cockroach, nearly as numerous as the cockroaches in the peak of Brockton Bay's worst months, some larger varieties of mosquito, flies I identified as the botflies that had come up in my research, and crickets.



No game changers, but I hadn't expected any.  The spiders were badass here, at least.  The silk wasn't so good, but even so, big spiders.



\emph{The Wards, their powers}, \emph{how to use them?  }I thought\emph{.} If I went by the PRT classifications, Tecton was a tinker with shaker capabilities.  Wanton was a breaker, someone who altered themselves or their relation to the world by some characteristic of his power, becoming a shaker effect, a telekinetic storm.  Annex was the same, only he became a living spacial distortion effect, a living application of Vista's power.  Golem, no doubt a shaker.  That left Cuff and Grace.  I wasn't sure how to peg Cuff, until I saw her in action, but she and Grace were both melee fighters in a fashion.



Of the six of them, four were shakers in some respect.  The classification included forcefields, effects like Grue's, and powers that reshaped the battlefield, like Vista's.



I'd been doing my reading on the PRT's terminology, among other things.



``Battlefield control,'' I said. ``You guys have battlefield control.''



``Lots,'' Tecton said.  ``Aimed for it.''



I gave him a curious look, but this wasn't the time for explanations.  I glanced at each of them in turn, so nobody would feel ignored, ``We could try to slow him down, but I'm not sure that's going to do much.  Instead, we're going to meet up with the Undersiders.  I think there has to be something we can do with them.  Citrine, maybe Grue.  They're versatile, and I've worked with them.   In the meantime, we're doing damage control.  Seeing what we can do to keep Behemoth-''



Another lightning strike made the ground shake.  Cuff shrieked, and I grit my teeth.  We barely had two seconds of reprieve between flashes of lightning.  They lanced down from the dark clouds of smoke overhead, more red than yellow, and the thunder seemed more intense than it should be.  That wasn't the worrisome part.  Behemoth was periodically hitting us with something bigger.  Bolts of lightning big enough to erase a small house from the landscape.



``-We're going to do what we can to keep him from murdering people,'' I completed my thought, belatedly.



``Right,'' Tecton said.



``You know about earthquakes and architecture, Tecton?''



``Yeah.''



``What can we do about the shockwaves, or whatever else he's been doing to make the ground shake?''



``I have ideas.  Not perfect, won't hold for long, but ideas.''



``Good.  And we were talking about lightning rods,'' I said.



``You said they don't matter.''



``The drones Dragon used redirected his lightning.  Golem?  How big can you go?  Optimal conditions?''



``Depends on the amount of space at the destination.  I'd need a big piece of solid material, and I'd need time.''



``We'll find an opportunity then,'' I said.  ``We'll figure out a way to make this work.''



The crash of something being knocked or thrown through a building half a block away nearly made me jump out of my skin.  The others had ducked for cover, too late to have mattered if it had been real danger.



``Keep moving,'' I ordered.



``Three of us are in heavy armor,'' Tecton said.  ``You can't really \emph{run} in armor like mine.''



``I get it,'' I said, even as I knew the Undersiders were getting further away.  ``Do the best you can.''



Mobility and transportations were problems.  I wondered if there were ways to fix that.  Even if we found Rachel and the others, I doubted we could put Tecton on a dog.  I couldn't remember which, but I sort of recalled that Wanton or Grace had been a little shy of the dogs, too, so that option was out.



But if we could make this work\ldots



Most people had evacuated at this point, with only a handful of stragglers occasionally passing us, giving us wary looks.



I drew arrows in the air to direct the remaining civilians away from the stampede of people, putting them on a general route where smoke didn't seem to be heavy, and where I hadn't been able to see or sense any fire.



Other heroes were joining the fray.  I saw Eidolon pass overhead, surrounded by what looked like a shimmer of heat in the air.  A forcefield?  Something else entirely?  If there were more with him, I couldn't see them through the smoke.



I resumed my recon, continuing to expand the swarm that was keeping me company.  My range was extensive, now, with a radius of maybe one thousand, eight hundred feet.  That extended a fraction further as I zig-zagged over the area, picking up more bugs on the fringes and bringing them to me.



I stopped when I saw a short crane, three or four stories tall.  I turned around to meet the others, perching on the corner of a rooftop.  I pointed the way with ambient bugs, ``Tecton, this way.  Take a shortcut, right through the building.  I don't want to lose any time if we can help it.''



``Right,'' he said.



It took only a minute for them to reach the crane.



``We've got two people who can distort metal,'' I said.  ``Annex and Cuff.  Maybe Wanton can help too.  Tear it down.  We're making our lightning rod.''



``You sure?'' Tecton asked.  ``Because this makes a pretty good lightning rod on its own.''



I glanced nervously over in the direction where the smoke and lightning flashes were most intense.  If he shot us, right here, right now, and turned the crane into a tesla tower, this might be my dumbest move yet.  I perched on the corner of a building, where I still had a measure of cover, and watched the battle in the distance.  I could see Legend's lasers through the smoke, hundreds at a time, radiating out from one central point, from Legend himself, and then turning sharply in the air to strike Behemoth.



Behemoth was using flame, which was some small reassurance, and he was occupied with the two remaining members of the Triumvirate.



``Yeah.  Do it.''



Both Annex and his costume merged into the base of the tower, and gradually climbed up to the point where the upper part still stood.  He could only `annex' part of the object at one time, it seemed.  No surrounding a whole building.  He set about breaking the bonds, and the crane's arm began to bend.  Cuff caught one end of it, then began heaving it towards the tower's base.  The other half snapped off, and Annex helped guide it down, sliding it against the crane's shaft.



It was costing us time, this project.  I felt impatient, was worried it wouldn't work, and these would be wasted minutes we could be doing something else.



But they were making it happen, putting the pieces of our project together.  Cuff was walking around the crane's base, effectively melting the metal, or reshaping it so it formed a flattened blob.  Annex tore the rest apart, so Cuff had more material to work with.



When Cuff was done, Annex slipped down to the blob and flattened it out further.



``A little thicker,'' Golem said.



Annex `swam' around the blob's perimeter, shifting more material towards the center.  Cuff drew a blob of metal out of the pad and shaped it into a disk for Golem.



``A lot of synergy in this team,'' I commented.



``Sort of aimed for that,'' Tecton said.  ``They took everyone willing to leave Chicago, to support other cities that lost more members, offered incentives to the rookies if they were willing to move to another city.  Your-parents-can-afford-not-to-work-for-a-year kind of incentives.  I drafted these guys because I thought their powers would work well together.''



``Drafted?'' I asked.



``Yeah.  I mean, most teams are lucky if they get a few members with a good interaction, with some more on the fringes that they have to work around and fit into the mix.  We had a good setup with Raymancer, before he got too sick to move.  A strong, versatile ranged attacker with the rest of us situated to protect him, right?''



I nodded.



``After seeing the Undersiders at work, I started to think we need to be less mix-and-match.  Form teams with specific goals in mind.  New York sort of does that.''



``I know they have a team of `lancers'.  Forward vanguard, fast moving.''



``Exactly, and they're also considered one of the better teams.  Maybe we all need to do that.  Except New York can do it because they've got a lot of capes.  Rest of us are making do.  Other team leaders are going for versatility, to cover every base.  I say fuck that.  We build around a concept, a game plan.  Once I decided on that, I went out of my way to ask for Annex, even though another team had already picked him up.  Made my argument, Chevalier gave the a-ok.''



``And where do I fit in?  Defiant said you were the one team that seemed interested in including me.  I guess I \emph{sort of} fit into a shaker category, in a roundabout way.''



``That, and we've fought on the same side.  I saw what you managed with Clockblocker's power and yours.  You stopped Alexandria, too, and all that other stuff we were warned not to bring up.''



I tilted my head to indicate mild confusion.



``They didn't want us to mention how you've kicked ass as a villain.  Way Revel explained it, they wanted to see if you'd boast about it, to see just how badly you wanted a leadership role, where you'd get frustrated and how you'd act.''



I frowned behind my mask, but I didn't comment.



``Anyways, the problem with this team going this route, focusing on the one thing, is we're very weak against certain approaches, strong against others.  We need a certain kind of leader for that, and I know you pulled it off with the Undersiders.''



``I hope I can live up to that kind of expectation,'' I said.



``I know it's lame of me, that it might look like I'm trying something experimental and setting you up to take the fall if it fails-''



``No,'' I told him.  ``I don't get that vibe.''



The ground tremored.  I worried briefly that the construction would tip, but it didn't.  How long would it stand tall once it was at its full height?



``Good,'' he said.  ``Because that's not what I'm doing.''



I was watching the others work, The pad of metal was about twenty feet across, now.  A circular disk with a flat surface on the top.  ``Okay.  I think I can play ball, if that's the case.  It's good.  I like your line of thinking, about the team.''



He offered me a `heh' before answering, ``Of course.  I'm a pro when it comes to putting stuff together.''



``Putting \emph{buildings }together,'' Wanton chimed in, forming back into his real body.  Dust billowed around his feet.



``That's my power, but I'm not limited to that,'' Tecton said.  ``You guys don't need any help?''



``Save your juice.''



Golem started to put his hand into the plate of metal he'd been given, then hesitated, ``I won't be able to move my hand once it appears, if I go this big.  What shape should my hand be?''



``Middle finger extended,'' Grace suggested.  ``A big `fuck you' to the Endbringer.''



``That'd look bad for the PRT,'' Tecton told her.



``Tell them it's the most efficient form,'' she said, with a shrug.  ``Have to make it as tall as possible.''



``No,'' Tecton said.  ``Index finger would work nearly as well, and New Delhi might take offense at a metal statue of an obscene gesture in the middle the disaster area.''



``A `v','' Cuff suggested, making the gesture with her index and middle fingers.  Her voice was shaky, her confidence rock bottom.  ``For victory.  Almost as good.''



``A `v' for victory,'' Tecton answered, ``Good.  \emph{Thank you}, Cuff.''



\emph{That's really lame}, I thought, but I held my tongue.  Too easy to become the bad guy, here, and it was a resolution to the stupid, petty argument, giving us the chance to move on.



Cuff smiled a little in response to the praise, though, then winced as Grace punched her in the arm.  I heard Grace mutter, ``Spoilsport.''



Cuff's smile returned to her face a moment later.



\emph{And maybe it's good for Cuff, to have something constructive to offer.  }She looked a touch more confident, smiling nervously as she followed Grace.  Cuff didn't seem like she was growing numb to the sounds or vibrations of the destruction Behemoth was inflicting on us.



Golem started to push his hands into the plate.  The gauntlet's fingertips were already emerging, a mirror-replica to Golem's own gauntlet.  A hand half as wide as a house, slowly rising from the platform.



Annex dove into the ground, and circled the platform, binding it to the street.  He disappeared beneath the ground, then emerged a few seconds later, pulling his cloak tight around himself.  ``Reinforcing, so it doesn't fall over on us.  Also, brought a spike of metal into the ground.''



``I can help,'' Golem said.  He reached his other hand into the ground, and a smaller hand fashioned out of pavement lurched out of the ground to rest against the base of the arm.  He withdrew his hand, leaving the pavement hand in place, then repeated the process, until six arms were supporting the spire.  ``Not sure how well that works as it grows.''



``Good job, both of you'' I said.  I held my breath as the wind brought heavy smoke past us, waited for it to dissipate.  There were too many variables to cover, and I wasn't sure enough about this squad to believe I'd accounted for all of them.  ``Can you move while carrying the plate?''



``Think so,'' Golem said.



``Let's go, then.''



``Starting to realize why all the capes are so fit, looking good in the skintight costumes,'' Golem huffed, as we made our way towards Behemoth.  ``So much running around, the training, constantly going places, never time to have\ldots decent meal\ldots''



He trailed off, too out of breath to speak.  I eyed him.  The armor made it hard to tell, but he might have been somewhat overweight.



The hand rose into the air, a virtual tower, as we made our way towards the battlefield.  Golem had to push his hand in gradually to achieve the effect, and it disappeared into the panel.



It was working, though.  For better or worse, they'd created a spire, a replica of Golem's hand, spearing more than fifty feet in the air, with more room to grow.  Sixty feet, a hundred\ldots



A lightning bolt lanced out from the midst of the cloud of smoke, striking the hand.



There were whoops and cheers from the Chicago Wards.  I managed a smile.



Another lightning strike, curving in the air, hit the hand.  Residual electricity danced between the two extended fingers.



It was working, and as much as it was a success in helping against the lightning, it was working to help morale.  To contribute something, \emph{anything}, it mattered.



``Air's ionized now,'' Tecton said, as if that was a sufficient explanation for everyone present.  I got the gist of what he meant.  The lightning would be more likely to strike there again.  Lightning \emph{did} strike the same place twice.



I took flight.  The Wards took my cue and followed on foot.



We found the Undersiders at the very periphery of the battlefield.  They had collected a group of wounded Indian capes and were draping them across the backs of one of the dogs.  Two uninjured Indian capes were looking very concerned, staying at the dog's side.



I landed beside Grue.  He'd used his darkness to form a wall.  I wasn't sure what it was for, but the smoke didn't seem as bad here.



``Skitter,'' he said.



I didn't correct him.  \emph{You'll always be Skitter to me}, he'd written.  Or something like that.



``Got a plan?'' I asked.



``Dealing with the wounded,'' he said.  ``Nothing else.''



I studied him.  I could see how defensive his body language was, his glower, the way he moved with an agitation that didn't suit him.



Was he not holding it together a hundred percent?



``Where's Tattletale at?''  I asked.  ``I kind of got distracted as everyone was moving out.''



``At the command center with Accord.  She just contacted us through the Armbands.  They're waiting to talk to Chevalier, fine tune the defenses.  Accord thinks he can layer the defenses to maximize the amount of time we buy.  Scion was occupied with some flooded farmlands in New Zealand, flew towards South America, last they saw.  Wrong direction.''



I nodded, my heart sinking.  It didn't seem we'd be able to count on him.  Not any time in the immediate future.  ``And Parian, Foil?  Citrine and Ligeia?  With Accord and Tattletale?''



``No.  Those four split off into another group.  They can put out fires, and Citrine can protect them from lightning strikes so long as they aren't moving around too much.  Flechette's using the opportunity to shoot him, for all the good it's doing.  Our group wouldn't be any use to them, so we're doing what we can here, a little further away.''



``Got it,'' I said.  ``You have a way of communicating with them?''



He tapped his armband, then pressed a button.  ``Relay this message to Citrine.  All well, Skitter and Chicago Wards just arrived.  Inform as to status.''



There was a pause.



``\emph{Message from Citrine,}'' the armband reported, the voice crackling badly.  Then the crackling redoubled as the voice stated, ``\emph{Status is green}.''



``Any objection if we assist your group?'' I asked him.



Grue shook his head.  He started to reply, but was cut off as Behemoth generated another shockwave.  A rumble drowned everything out, as every building without something to protect it fell.



``No objection,'' Grue said, when the rumble had dissipated.  He echoed my question from earlier.  ``Got a plan?''



``I wish,'' I said.  ``More lightning rods, maybe, if we get the opportunity.''



The smoke was clearing towards the battle's epicenter.  Legend and Eidolon were a part of that, as were the craft that supported them.  The fires were dying out, extinguished or stamped out.



Behemoth wasn't \emph{that }tall, hard to make out above the buildings that still stood.  I chanced a look, and flinched as another bolt of electricity made its way to the lightning rod.



\emph{The path of least resistance}.



Behemoth had noticed that time, or he'd decided to do something about it, because he lashed out at Legend and Eidolon once more, driving them back, and then made a beeline for the structure. He threw electricity outward, two bolts, continuous in their arc, and they briefly made contact with the tower.  A second later, they broke free of the tower's draw.  He was paying attention to where he was shooting now, not simply striking across a distance with the goal of setting indiscriminate fires.



Fire roared around Behemoth as he got away from the area that had already been scorched and blasted clear of any fuel sources.  His dynakinesis fueled the flames, driving them to burn hotter, larger, and with more intensity.  With a kind of intelligence, the fires spread to nearby buildings, ensuring that no place was safe, nor untouched.



I could see the blaze making its way closer to us.  Not a concern in the next minute, maybe not even the next \emph{five}, but we'd have to move soonish.



Legend and Eidolon hounded the Endbringer, Legend initially a blur that couldn't even be pinned down long enough to strike, even with lightning.  As the hero flew, he filled the sky with a series of lasers that raked Behemoth's flesh and targeted open wounds to open them further.  When Behemoth turned away to deal with Eidolon, Legend slowed, and the lasers grew in number and in scale.



``What's with the hand shape?'' Regent asked, as he poked his head out from cover enough to peek at the scene.



``A `v','' Golem said, his voice small.



``I get it.  You're calling Behemoth a big vagina.''



``It's for \emph{victory},'' Cuff said, sounding annoyed.



``That's lame,'' Imp said.



``\emph{Really} lame,'' Regent echoed, ``I prefer the vagina thing.''



``Way you dress,'' Grace commented, ``I wasn't so sure.''



``Ohhhhh,'' Imp cut in, she elbowed Regent, ``Ohhhhh.  You going to take that?''



Regent only laughed in response, shaking his head.



``Is the little princess feeling brave?'' Grace taunted Regent.  ``Come on.''



``It's for `victory','' Cuff said, her feeble protest lost in the midst of the exchange, and in that instant, she sounded surprisingly young, vulnerable.



``No fighting,'' I said, \emph{have to stop this before it escalates}.  ``Regent, stand down.  Grace, you too.''



Regent snickered under his breath.



``And no more banter,'' Grue said.  ``There's more people to help.  Move.  With luck, those guys can keep him busy long enough for us to clear out.''



``Team's mommy and daddy, reunited,'' Imp commented, adding an overdramatic sigh. ``\emph{So }awesome.''



``I'll point you guys to the wounded,'' I said, not taking the bait.  ``Go.''



``No saying or doing stuff that'll get us killed, like saying goodbye or getting laid,'' Regent commented.  ``There \emph{are} rules.''



``Get us killed?  What's Weaver doing?'' Cuff asked, sounded alarmed and confused.



Regent glanced at her, ``I'm just saying, Grue's already screwed, he's not a virgin, he's bl-''



Grue struck Regent across the back of the head.  The crown and attached mask were moved slightly askew, and Regent fixed them.  He told Cuff, ``Regent's being an idiot.  Ignore him.  Now \emph{go}.''



``This way,'' Tecton said, setting a hand on Cuff's shoulder, ``Opposite direction from Regent.''



Imp started to turn around to follow the pair, grabbing Regent's wrist to pull him after her.  Grue stepped in her way and physically turned her back around.



``Sorry for our contribution to that,'' Tecton said.  ``Grace gets hard to handle when she's stressed.''



``I understand.  Regent and Imp\ldots'' Grue started.  ``Really have no excuse.  That's pretty much the status quo.  They've been a little worse lately, but things haven't settled down since\ldots''



He trailed off.



``Since I left,'' I said.



Grue nodded.



Tecton nodded.  ``I get it.  Bygones.  We'll be back.  You okay watching the injured on your own, or-''



``We're good,'' Grue said.



Tecton left, with Cuff at his side.  Only Grue and Rachel remained, along with the Indian capes who were standing by the wounded.  Rachel was giving water to the injured who were capable of receiving it, the conscious ones, people with broken legs and burned hands.



I made eye contact with Rachel.  I wanted to ask how she was doing, knew she wouldn't like the implications that she wasn't peachy.



``I want to fuck this bastard up,'' she said.  ``Last one killed my dogs.  Killed Brutus, Judas, Kuro, Bullet, Milk and Stumpy and Axel and Ginger.  When do we attack?''



``I don't know,'' I said.  ``We'll try to find an opportunity.''



``And I get to do something,'' she said.



``I\ldots'' I started to voice a refusal, then stopped myself.  ``Okay.''



``Bitch, it'll be easier to collect the bodies if you take the dogs to them,'' Grue said.  ``Why don't you see to that?''



She glanced at me.  I resisted the urge to nod.  It would be an encouragement, without the complexities and ambiguities of speech, but it would also be supplanting Grue as leader, here.



Neither he nor she needed that.



``Sooner than later,'' he added.



She nodded.  Anyone else might have taken that as rude, but she accepted it without complaint.  She led the dogs away, and the Indian capes followed, not wanting to part from people who might have been teammates or family members.



When everyone was gone, Grue approached me.  I felt myself tense up.  Despite the adrenaline that already pumped through me, my heart rate picked up as he closed the distance.



He held my arms just above the elbows, very nearly encircling his middle fingers and thumbs around them.  Large hands, thin arms.  I'd put on a little muscle mass over the past few months, or he'd be able to do it for real.



And he rested his forehead against mine, as if he were leaning against me, despite the fact that he was maybe half-again to twice my weight.



It had been a long time since I felt quite so insecure as I had this past week.  As Skitter, I'd had a kind of confidence.  As Weaver\ldots I didn't yet feel on steady ground.



But in this moment, somehow, I felt like I could be his rock.



I wanted nothing more than to reach up, to put my hands around his neck, remove his mask so I could tilt my head upward to kiss him.  To give him succor in basic, uncomplicated human contact, at a time he was on unsteady footing and couldn't even say it aloud.  I stayed where I was, our foreheads touching, my back to the wall, arms to my sides.  The masks stayed on.



The storm continued in the distance, and a detonation marked what might have been the destruction of one of Dragon's craft.  We didn't move an inch.



``I miss you too,'' I whispered.



He nodded in response, a hard part of his mask scraping against a part of mine.



I could sense the others gathering bodies, starting to make their way back here, to our rendezvous point.



``See,'' Imp said, appearing right next to us, ``This is \emph{exactly} what Regent was talking about.''



``We weren't doing anything,'' I said.  I pulled away from Grue, annoyed.



``You were \emph{being sweet}.  That's probably a death sentence.''



``They were snuggling?'' Regent asked, rounding a corner.



``\emph{Christ},'' Grue said, under his breath.  Firmer, he said, ``Enough of that.''



Imp only cackled, and she kept cackling.  I was pretty sure she prolonged it just to be annoying, stopping and starting again until Rachel and the last of the Wards returned.



``Let's talk plans,'' Grue said.  ``We've got a good roster here.  Two teams.  Almost three full teams, if we pick up Parian, Foil and the Ambassadors.''



\emph{He sounds more confident.  A little more balanced.  The agitation isn't so obvious}.



``There's more wounded in the area,'' I said.  ``And we're running out of space.  Each dog that's loaded up with the injured is a dog you guys can't ride.  Fires are getting closer, so we pick up everyone we can, load them onto makeshift sleds, then hurry back to a place where we can get them medical care.''



``It's a plan,'' Grue said.



``And,'' I said, ``We need to find a better use for our strongest members.  Citrine could be useful.  Grue?  If we get the sled going, you stay close to the wounded.''



He turned his head my way.



``We have about twenty here.  Six or so capes.  Maybe one's got a power we can use.''



He nodded.  ``I already checked most.  But I can use a power from the back of the sled without blinding anyone.  It works.''



``There's a joke there,'' Regent said, ``But-''



``\emph{Don't},'' Imp said.



``I wasn't going to.  It's crass, totally inappropriate, and I'm better than that.''



``You're going to,'' Imp said, stabbing a finger at Regent's chest.  ``You were going to say something about Grue going to the back of the bus, and you can't let it go.  It'd be lame and \emph{really} tasteless and \emph{too far}, and it'll start the sort of fight that isn't fun or funny.  I'm calling it: you'll hold it in until you can't help but say it.''



``Well I'm definitely not going to say it now that you've \emph{spoiled} it,'' Regent said.  ``No shock value, no people feeling bad because they inadvertently laughed at something fucked up.''



``You two go squabble somewhere else,'' Grue said.  He glanced at me.  ``There's more bodies to collect?''



``Too many bodies,'' I said, my voice sober, ``Not many injured left who haven't already been carried away by friends, family and neighbors, or who aren't in such bad shape that they can't move.  Maybe six more we could load up, if we're going to get out of here in time.''



``Go,'' Grue said.  ``She'll show you the way.''



``\emph{Run},'' I said.  They didn't have to run, but it got rid of them sooner.



``\emph{Children},'' Grue muttered under his breath.



``Wards,'' I said.  ``If you aren't making the sled, go get the rest.  I'll help.''



My team left Annex and Cuff behind while we collected the wounded.



The one I was helping was a child, burned.  She wasn't any older than ten.



She said something incomprehensible.  Another language.



``English?'' I asked.



She only stared at me, unable to understand me any more than I understood her.  Her eyes were a little glazed over, but the pain in her expression and the fear suggested that the benefits of being in shock were receding.



A part of me felt like I should have helped her sooner, but it wasn't a logical part of me.  There was so little I could do, and it didn't matter if I did it before or now.  And maybe a small part of me was putting it off because it wasn't going to be pretty.



``I'm not that scary,'' I said, ``Okay?''



I pulled off my mask.  ``See?  Ordinary person.''



Her expression didn't change.



``I'm going to have to move you,'' I said, and the words were for me as much as they were for her.  I kept my voice gentle, ``It's going to hurt, but it'll mean we can get you help.''



She didn't react.  I studied her.  Blisters stood out on her arms and neck, and on the upper part of her chest.



I could maybe understand a little of Rachel's anger at the loss of her dogs, seeing this.  Behemoth probably hadn't even given a coherent thought to the pain he'd inflicted on this girl, on countless others, just like Leviathan had mindlessly torn through Rachel's dogs.



\emph{Why?}



Why did the Endbringers do this?  Were they part of the passenger's grand plan?  Cauldron's monsters, taken to an extreme?  Tattletale had said they were never human, but she'd been wrong before.



Or maybe I hoped they had been human because it was an answer, because the alternative meant I didn't have enough data points to explain it.



With as much gentleness as I could manage, I moved bugs over the girl's body.  She reacted with alarm rather than pain, and I shushed her.  The bugs were spreading possible infection, no doubt, but I suspected infection was inevitable, given circumstance.  Using the bugs let me know where the blisters were, where the skin was mottled with burns.



I took off my flight pack and flipped it over.



\emph{Like ripping off a bandaid}, I thought, \emph{only it's at someone else's expense}.



I lifted her, and she shrieked at the physical contact, at the movement of burned flesh against clothing and the ground.  I set her down on the flight pack, placing a hand on her unburned stomach to stabilize her.  I activated the left and right panels, gently, so it had a general lift without any particular direction, and I led her to the sled in progress.



Golem had already returned, and the three of them were combining powers to make the sled.  Cuff was feeding the chain Rachel had provided into loops at the front.



With Grue's help, I eased the girl down from the flight pack, setting her with the other wounded.



``We're going to hurt him,'' I said, retrieving the flight pack.



``Behemoth?'' Cuff asked me.



``We're going to find a way,'' I said, and that was all.  I met the little girl's eyes.



Cuff followed my gaze.  ``I guess I''m on board with that.''



``Why did you come?''  I asked.  ``I mean, I get why we all came, on a level, but\ldots no offense, you're in a totally different headspace.''



``For my mom and dad,'' she said.



I glanced at her, but she didn't elaborate.



It took another minute to get the sled prepped and people mounted.  Rachel enhanced the size of her dogs so they'd have the strength to pull not only the wounded, but the two teams as well.  It meant they were slower, but it also meant moving nearly forty people with four dogs.  I took off, flying, leading the way and giving directions with bugs as they followed.



A crash heavier than any we'd had yet made the dogs stumble, falling.  It very nearly overturned the sleds.  Bitch had fallen from where she sat on Bentley's back.  I stopped at her side to make sure she was alright, gave her a hand in getting back to her feet.  She accepted it without complaint or incident, but when she met my eyes, her glower cut right through me.



Was that her resentment at work or my guilt, that made me feel that way under her gaze?



Once I'd verified that no damage had been done, I rose just high enough to peer over the top of a building.



The lightning rod had tilted, leaning against an adjacent building, the supports Golem had raised had crumbled.  Behemoth, too, had fallen.



Eidolon and Legend hovered in the sky, flanked by four dragon-craft.



Another figure was there as well, hovering where Behemoth had been standing an instant ago.  The Endbringer had been toppled with one massive blow.



I touched the button on my armband, lowering my head beneath cover.



``Send this message to Defiant,'' I said.  ``You said she was dead.  You said you verified.''



The reply crackled so badly it was almost inaudible.  ``\emph{Reply from Defiant.  I saw the body myself, we checked her DNA, her \ldots readings, we matched against the mountings for her prosthetic eye \ldots carbon dated it to verify.}''



He didn't even need to ask who I meant.



I pressed the button, ``Ask Defiant who the hell that's supposed to be, if it's not Alexandria.''





