





If I'd had any doubt it was Alexandria, it was banished when she followed up the attack.  Behemoth started to rise to his feet, and Alexandria struck.  It wasn't a punch with a great deal of wind-up, and she only crossed fifty or sixty feet before driving it home, but the impact was undeniable.



Behemoth absorbed the blow, and redirected it into the ground.  He didn't move, as though the blow had never struck home, but the ground around him shattered like the surface of a mirror.  Fragments of rock and clouds of dust flew up around him, and a three-story building on its last legs tumbled over.  The damage to the ground made him sink a fraction.



I could see the change in the Endbringer's demeanor.  Before, he'd been wading forward, as if Legend, Eidolon and the metal suits were little more than a strong headwind.  He was moving with purpose now, with an opponent that was veering in and out of easy reach, one he could hit, without Legend's speed or Eidolon's personal shield.



She had told me that they knew how to fight each other, and I could see that at play, here.  Part of the change in Behemoth's approach might have been that interaction at play.



It was a fight involving four individuals who couldn't hope to do substantial damage to their opponents.  The dragon suits and other capes were a peripheral thing.  Alexandria circled, just beyond the perimeter of Behemoth's kill range, her teammates and their supporting cast bombarding him in the meantime.  They destroying the ground beneath his feet, trying to get him when his focus was elsewhere and his ability to redirect the energies of a given attack was reduced.



He couldn't keep her in mind at all times.  She waited until he focused on a different combatant, heaving out lightning or creating flame to attack the ones in the air, and then she struck.  Nine times, he simply deflected the strike into the ground, as a rumble and a series of spiderwebbing cracks in the streets, or into the air as a shockwave.  Again and again, he came within a heartbeat of getting his hands on her in retaliation, not even flinching as she struck him, reacting with an unnatural quickness as he reached out, to try to pin her using his claws, to strike her into the ground or to time the collapses of buildings to briefly bury her, so he could close the distance.



The times her strikes did get past his defenses, her tiny form in the distance with the black cape trailing behind her lunging into his kill range to deliver a blow or a series of blows, Behemoth stumbled, caught briefly at the mercy of physics.



In a fashion, she was doing the same thing the lightning rod had been, buying all of the rest of us a small reprieve.  There was no guarantee, and there wouldn't be any until he was driven off or we moved a hundred miles away, but she was making the rest of this just a little easier, reducing the destruction just a fraction unless he specifically took the time to work around her.



Was she being more cautious than she needed to be?  I saw her pass up on a handful of opportunities I might have taken in her shoes, when his back was turned, his attention sufficiently occupied.  Was she aware of something I wasn't?  Was she a convincing fake?  Or was she just a little more \emph{afraid}, after what my bugs had done to her?



However effective the distractions, he was still Behemoth, still implacable, a living tank that could roll over any obstacle and virtually any individual, unleashing an endless barrage of artillery at range.  He reached the lightning rod and shoved it to the ground.



I was reminded of my teammates, descended to the ground, where they were still getting sorted.  The chains that led from the dogs to the harness had tangled.



``What the hell was that?''  Tecton asked.



``Alexandria,'' I said.



``You murdered Alexandria,'' Regent commented.  ``Remember?  You're a horrible person, doing things like that.''



``You leave her alone!''  Imp said, uncharacteristically.  ``She feels so bad she's \emph{seeing} things.''



``Can we \emph{try} to stay serious?''



``Don't be too hard on them,'' Tecton said.  ``Some people use humor to deal with bad situations.''



``It's true,'' Regent said, affecting a knowing tone.



``No,'' Grue responded.  ``They're just idiots.  You two keep your mouths shut.  The adults are talking.''



Imp raised her middle fingers at him.



He turned to me, ``It's Alexandria?  You're sure?''



``Can you ever be sure of anything?  Clones, alternate realities, healing abilities\ldots there's any number of possibilities.''



In the distance, a glowing orange sphere flew into the sky.  It reached a peak, then descended, crashing into the distant skyline.



I reoriented myself and flew up to the edge of the roof to peek at the battle.  Behemoth had melted down part of the metal arm and fashioned the melted metal into a superheated lump.  A second lump, cooler and not yet fabricated into an aerodynamic shape, was sitting beside him.  Alexandria tried to strike it away, but he caught it with one claw.  He superheated it, shielding it from Legend and Eidolon's fire with his body, then heaved it into the air.  The projectile flared intensely as it left his kill range, following nearly the same path as before.



Lasers from capes in the distance sliced the second sphere into shreds before it could strike its intended target.



Grue tugged the chain.  He looked at Rachel, who only nodded.



And we were moving again.



I returned to my recon position, scouting to ensure the way was clear, keeping an eye on the fight and ensuring that there weren't any attacks coming our way.



Behemoth was \emph{glowing, }his gray skin tending more towards white, a stark contrast to his obsidian horns and claws.  The heroes were backing off a measure, and Behemoth was taking advantage of the situation to stampede forward, tearing past buildings and barricades.



``Grue!''  I shouted.  The noise in the distance was getting worse.  If Behemoth was continuing the path I'd seen him traveling, he was wading through a series of buildings.  Grue didn't hear me.  I raised my voice, waited until the noise died down, ``Radiation!  Use darkness!''



He did, and we were cloaked in it.  I continued navigating, using my bugs this time.  Only a small handful ventured forward at a time, checking for fires.  I was flying blind, scouting without the ability to see.



It delayed me when a fire \emph{did} present itself, and I was delayed even further when I faced the issue of trying to communicate it to the team.



``Fire!'' I shouted.  I knew he could hear me through the darkness, but he couldn't hear me over the sounds of toppled buildings.  I was no doubt drowned out by the sound of the sled scraping against the road, the crashes in the background and the rushing of the wind.



I changed direction, aiming for the sleds, and flew forward.  \emph{A little off target}.  Didn't want to knock someone off the sled.  I made a slight adjustment with the antigrav, and landed on the front edge of the sled, between Grue and Rachel.  Grue very nearly let go in his surprise, and I caught the back of his neck to keep him from falling off the sled.



He left the darkness to either side of us intact and created a corridor.



``Fire!'' I said, the instant I was able.  ``Just over that hill!  Go left!''



He cleared more darkness, and we turned sharply enough that the sleds swung out wide.  I held on to the lip of the sled, but I let myself slide back, using the antigrav pack to keep myself from falling to the road.



The sudden movement had shifted the occupants.  The design of the sled made it difficult for anyone to fall out, but they'd slumped against one side, and one man was hanging halfway out.  With only one usable arm, he wasn't able to maintain a grip.



The sled went over a series of bumps, and I reached him just in time to give him the support he needed, one hand and both feet on the lip of the sled, the other hand holding him.



Once they were on course, I helped ease him down to a better position.



He said something that I couldn't understand, his words breathless.



I took off.



A shockwave ripped past us, harsher, briefer and more intense than a strong wind, not quite the organ-pulverizing impact it might be if Behemoth were closer, or if there were less buildings in the way.  I ventured up to a rooftop where I might be able to see beyond the darkness.



The shockwave had parted the clouds of smoke, but they began to close together once again.  I could make out a form, maybe one of the Indian capes, swiftly growing.  Ethereal, translucent, his features vague, the light he emitted only barely cutting through the smoke cover.  He slammed hands into Behemoth's face and chest.



Behemoth parted his hands, then swung them together.  I didn't wait for them to make contact.  I ducked behind cover before the shockwave could hit me directly.  All around me, the smoke was dashed out of the sky by the impact's reach.  With the front of my body hugging the building, I could feel not only the shockwave, but the vibrations that followed it, as buildings fell and debris settled in new locations.



He delivered shockwave after shockwave, and I was forced to abandon the cover of the building for something a little more distant.



He wasn't irradiated any more.  Or, at least, the glow wasn't there.  He'd been buying himself a reprieve from the assault of the heroes, a chance to cover more ground.  Now they had resumed the counter-offensive.  The noises of the fight followed me as I got ahead of the Undersiders.



Another obstacle.  A crowd, this time.



I landed on the sled once more and ordered a stop.  It took a second for the dogs to slow down enough.



Locals stood in our way.  Some had guns.  They ranged the gamut from people a step above homelessness to businessmen.



``Leader?'' one asked, his voice badly accented.  He was younger, very working class, which surprised me.  I'd anticipated that someone older and more respectable would be taking charge.



``Me,'' I said, using a small boost from the flight pack to get ahead of the group.



``Stealing?'' he asked me, his voice hard.



``No.  Injured.''



He gestured towards the sled, taking a half-step forward.  I nodded.



I didn't like wasting time, but I was hoping he'd give the a-okay and the group would get out of our way.  I watched as he studied the people lying in the sled.



``We take,'' he said.  ``We have doctor, hiding place.  You go fight, help.  Is your duty.''



I could sense a group approaching from Behemoth's general direction.  Two women in evening gowns, a girl in a frock, another girl in costume.



No time to dwell on decisions.  I asked the man, ``You sure?''



``Yes,'' he said.



``Cuff, Annex, kill the chains.  Leave sleds behind.  Wards, stay with me.  Grue, I'll direct you guys to the Ambassadors.  Take the dogs.  Leave us some darkness for cover so we're safe from any more radiation.''



It took only a few seconds to get organized.  By the time the Undersiders had departed, we had a team of people pulling the sleds.



``\emph{Message from Defiant},'' my armband declared.  ``\emph{Alexandria confirmed gone from PRT custody.}''



``Fuck,'' I muttered.



``Message from Defiant.  \emph{Stay out of her way until we know more.  Behemoth's approaching the first perimeter.  I will keep you posted.}''



``Tell him thank you.''



``It's a good thing,'' Grace said.  ``Maybe not in the long run, but for now-''



``For now it's an unknown factor,'' I said.  ``And there's one really big \emph{known} factor that's tearing through this city, and we should be devoting all our attention to it.  To Behemoth''



``We can focus on both,'' Tecton said.



``That's how you get blindsided,'' I told him.  I hauled on the chain, and the sled moved.  Cuff seemed to be doing the lion's share of the work, standing between the sleds and ushering them forward.  Though it screwed up the direction the sleds were facing, making them veer left or right, it gave us enough momentum that we only needed to work on keeping it going.



We reached a squat building with signs featuring unintelligible writing and cars.  Some hurried forward and opened a garage door, and we kept the sleds on course to lead them inside.



Their `hiding place' was an underground corridor, leading beneath and between two hoists for the cars.  Annex had to reshape the sled to fit, and we found ourselves on a general downward incline.  People shifted position to the sides of the sled to keep it from getting away from us and running over the people in front.



I saw the man who'd done the talking glance down at the wounded.  His eyes caught the light in a way that reminded me of a dog, or a cat.



\emph{Capes.  At least some of these guys are capes}, I thought.  The `cold' capes, the underworld's locals.



It was an ominous realization, as we descended, to know that we were outnumbered by parahumans I knew nothing about, with unknown motives.



The armband's crackling was getting steadily worse.  ``\emph{Message from Grue.  Rendezvous is fine.  On way to your location.}''



``Message received,'' I replied.



``\emph{Message from Grue\ldots}''



The voice devolved into crackling.



Too much ambient electromagnetic radiation, and the amount of ground that was between us and Grue probably didn't help.



It was hard to gauge how deep we were getting.  We reached a point where a fissure made moving the sleds more difficult, but Annex, Tecton and Golem shored it up in moments.



We descended deep enough that I wasn't able to access the surface with my bugs, then deeper still.



The more isolated we were, the more ominous the uncostumed capes around us seemed to become.  My bugs followed us down the corridor, just far enough back that the `cold' parahumans couldn't see them, close enough to help.



``This tunnel was made by a cape,'' Tecton said.



\emph{Don't bring it up}, I thought, suppressing the urge to react.



``No,'' the man with the eyes said.  He didn't turn our way.



I reached out and touched Tecton's arm.  He, naturally, didn't feel the contact through his heavy armor.  Tecton continued, ``I'm pretty s-''



My \emph{nudge} became a shove as I moved his arm enough to get his attention.  He looked at me, and I shook my head.  Tecton didn't finish the sentence.



``Oh so pretty,'' Wanton offered.



``Don't \emph{you} start,'' Tecton said.  ``The Undersiders are bad enough.''



I could see the Wards change in demeanor as we descended well beneath the city.  Tecton's head was turning now, scanning the people around us.  Wanton hunched over, as if the surroundings were weighing on him, a pressure from above.  Cuff had her arms folded, hugging her body, a defensive wall, however meager, against an attacker from above, and both Annex and Grace had gravitated closer to other team members, as if unconsciously adopting a loose formation.



Golem, odd as it was, seemed to fall more in line with Tecton and I, watching the surroundings, eyeing the strangers who accompanied us.  It wasn't that he wasn't \emph{afraid}; everything \emph{else} about him suggested he was.  It was more that he was wary in a natural, practiced way.



How had he picked that up?  He was supposed to be a rookie.



I held my tongue and used my bugs to scan the surroundings.



The area opened up into an underground living space, crowded with weary and scared people.  It was dim, with lights alternating between floor and ceiling positions, tight corridors with what seemed to be tiny apartments carved out of the rock.  My \emph{prison cell} had more space than these quarters.  At least there was room to stand straight up in the jail.  These rooms were stacked on top of one another, two high.



But it was space nonetheless.



``Is it stable?'' I asked Tecton.



``I can't see enough to tell,'' he said.  ``Maybe?  Probably?''



``I don't know if I can leave people here if it's a deathtrap,'' I said, as I eyed the people emerging from the rooms.



``Pretty risky up there,'' Wanton said.



\emph{Up there there's a chance.}  I was counting hundreds or thousands down here.  My bugs could sense corridors, and I was left wondering if this was only one area of many.



Some of the residents stepped forward to help, hands on weapons or simply watching us, undecided on whether we were threats or not.



The leader, who I was mentally labeling `Cat's Eyes', said something, and they relaxed a fraction.  He said something else, and they started helping the wounded.  None used or displayed any overt powers.



``Done,'' Cat's Eyes said.  ``You go.  Fight.''



Defiant had said we needed their assistance.  ``We need your help.  You and any of the others with powers.''



He narrowed his eyes.  Except that wasn't the sum total of the change in his expression.  His face \emph{hardened}, drew tighter, high cheekbones somehow more prominent in the dim, lips pressed together.  ``No.''



``No?''



``Not our duty.  \emph{Yours}.''



``It's everyone's duty.''



``We handle enemy you don't see, you costumes help enemies above ground.  Scare \emph{Prathama} away.''



\emph{Like it's that easy}.  ``We need your help.  Everyone's help.''



``No.  We show ourselves, and all ends badly.  We fight \emph{subtle} war.  Better to lose today and fight subtle war tomorrow.''



\emph{Better to let Behemoth win than to show themselves and lose whatever edge they hold against their current enemies}?



``You see me, I am done.  Finished.  You see all of us, they are done.  No.''



Maybe India had its own share of capes, on the same scale as the Slaughterhouse Nine.  Cleverer capes who worked in the background.



Or maybe they were just deluded, too set in their ways, afraid to fight and searching for excuses.



``Go.  Defeat him,'' he told me.



\emph{Grue was waiting}.  Or Grue was coming down here, maybe, with Rachel and the others.  If they saw him, an intruder without invitation, would they act?



``Okay,'' I said.  ``We need a vehicle if, um\ldots''



I trailed off as I mentally registered what my bugs were sensing.



A rush of cool, air-conditioned air in a space that had no right to have any, off to one side, the appearance of a person where there shouldn't be any.



``Weaver?''



I'd stopped talking, my attention caught by this visitor.  She was close.  All of the details matched the person I'd sensed inside the Kulshedra.  The clothes, the hair, the dimensions, even the way she moved.



Purposeful, unhurried.



``It's her.  The one who took Pretender.''



Everyone, myself included, tensed as she approached.  The foreign capes did it because she was an unknown variable.  The Wards and I did it because she was a \emph{known} threat.



She was older, but not \emph{old}.  Maybe my dad's age, maybe a little younger.  Pretty, in a very natural way.  She didn't wear any obvious makeup, and her black hair was somewhere between wavy and curly, a little longer than shoulder length.  Her features French or Italian, if I had to guess.  She wore only a simple black suit that had been tailored to fit her body, with a narrow black tie and a white dress shirt.  What got me were the eyes.  There was no kindness in them.



She spoke, but she spoke in a foreign language, and it wasn't to me.



Cat's Eyes hesitated, then gave her a reply.



``Who the hell are you?'' I asked the woman.



She glanced at me, and her gaze went right through me, as if I were barely there.  She turned her attention back to Cat's Eyes, said something else.



His eyes widened.



``You work for Cauldron,'' I said.



``Maybe we shouldn't taunt the bogeyman,'' Wanton chimed in.



``Bogeyman?'' Cuff asked.



``She's a hitman,'' I said.  ``Takes out anyone asking too many questions about Cauldron.  Or she \emph{was}.  Apparently she's gone after a lot of powerful capes, walked away without a hitch.''



My bugs gathered.  I could see the underground capes reacting, preparing for a fight.



``No,'' Tecton said, ``The truce.''



``I don't think she gives a damn about the truce,'' I answered.



``Until she breaks it, we don't break it.''



I didn't take my eyes off her as I murmured, ``Fun fact about life or death fights between capes.  You start letting your enemies make the first move, your mortality rate triples.''



``I gave the go-ahead for you to be acting leader,'' Tecton said.  ``Cool.  Lightning rod was fantastic.  But if we start a fight here and shit goes down, my ass is on the line too.''



``You're vetoing my order?''



``You haven't given an order yet, and no.  You've fought her, I haven't.  But I'm \emph{advising} you here.  Back off.  She hasn't done anything aggressive.''



\emph{``}She\emph{ will,}'' I said.



``Maybe,'' he said.  ``It's your call.''



I didn't give an order.  I watched instead.



She was speaking to Cat's Eyes in a low voice.  He was nodding unconsciously as she spoke.



Then she met my eyes.



``Who the hell are you?''  I asked.



``Doesn't matter,'' she said.  ``Go, Weaver.  Take your team.  We have no business with you anymore.''



``\emph{Anymore}?''



She only stared at me in response.



Damn, being on the receiving end of that stare was like being opposite Alexandria or Faultline in a bad mood.  I was starting to settle on the idea of her being a thinker.



She looked at Cat's Eye, ``It's time.  Tell them not to be afraid, and this will go smoothly.  Tell them to pass on the message so everyone hears.''



He nodded, then called something out in another language.  Others took up the call.



``Hold on,'' I said, raising my voice.



They didn't listen.  Why would they?  I barely had any clout.  The bugs around me were minor, all things considered.



I brought them closer, so they gathered at my feet.  She didn't even flinch.



One by one, portals appeared, rectangular doorways that were so bright they were painful to look at.  The smell of flowers, fresh air and nature flooded into the underground.  Every pathway and every available surface soon had one.  Nearly a dozen in my field of view alone.  My bugs could sense two dozen more in my range.



``No!'' I called out, once I realized what was happening.  I thought of what the Eidolon clone had said, about them experimenting on people, kidnapping people from alternate worlds.  ``You can't trust her!''



But the people here were scared.  Once the first few people tentatively made their way through, they ran for safety, running out into the open field, disappearing behind tall wild grass.



Cat's Eye turned to leave.



I reached for him, to grab his wrist before he could disappear.



The woman in the suit deftly deflected my hand, batting it aside.



``What the hell is Cauldron doing?  Do you want to start a war?''



She shook her head.  ``No war.  But we need soldiers.''



That was all the confirmation I needed.



``Wards!'' I called out.  My bugs and my Wards converged on her.



It mattered surprisingly little.  She stepped away from me, which I took as an excuse to close the distance.  If she wanted to get away, I'd get closer.  I worked to close the distance, using both the flight pack and my own two feet to draw in.  She stepped back out of the way, just out of reach of my strikes.



She swept her hands by the sides of her belt, and she was suddenly armed, if I counted a stiletto knife no longer than my finger and a handkerchief as weapons.



In the moment my swarm drew close, she stabbed the knife into a wall-mounted fire extinguisher.  The pressurized contents spewed out in a plume, collecting on my bugs and blocking their path.  It disabled the largest ones and killed the smallest, eliminating a good ninety percent of the bugs I had in reach in an instant.  I was forced to back off, so I didn't get the spray across my lenses or the fabric at my mouth.



She'd managed to avoid getting dirty, even.  I watched her from the other side of the spraying canister.  The direction of the plume and the hand with the handkerchief left her virtually untouched as Tecton drew close.  She danced back out of reach of his attack as he plowed past the spray.  Wanton had transitioned to the form of a localized telekinetic storm, and Annex had slipped into the ground, closing the distance to her.



If she was a thinker, someone relying on craftiness to win a fight, then I'd turn it into the kind of fight she \emph{didn't} want to participate in.  Tecton had power armor, Grace had super strength and Cuff had her metallokinesis.



I cranked up the flight suit and charged.  It was reckless, and it was hopefully the last thing she'd expect.  The goal was simple.  Close to melee, keep her occupied long enough for \emph{someone} to trap her.  With that done, we'd call each of the people she'd just contacted and bring them back to safety.



Assuming she was someone along the lines of Victor or \"{U}ber, a combat-oriented thinker, she'd try to do something like a Judo throw, redirecting my forward momentum to toss me to the ground.  I countered that particular maneuver by bringing myself to an almost complete stop before she could grab me, slipping to one side as Tecton closed the distance.



He punched, and she stepped back.  He extended the piledriver, a second punch without an instant of warning, and she evaded to one side.



\emph{A precog?}



I wasn't even finished the thought when she stepped around to Tecton's side.  He tried to body-check her, but she had a hand up to rest on his side, using the contact to brace herself, to push against him and leverage herself away.  She crossed one leg over the other to maintain an upright position, then brought herself into arm's reach of me.



Bugs exploded from the interior of my costume.  Spiders, hornets, wasps and beetles.  The only parts of her that weren't covered by the suit were her head and hands.  The hands were clasped behind her back before the swarm reached her.  A sharp toss of her hair swept them out of her way as she invaded my personal space.



Her hands, protected from my bugs by the simple obstacle of her torso, reached out, avoiding the worst of my swarm.  One caught the concealed flap of my mask, where it overlapped the neck of my costume, and pulled it down.  The other pressed the tip of the stiletto knife to my jugular.



My team, just a moment behind me and Tecton in their intent to engage her, froze.



Fuck me, I had ten thousand bugs here, easy.  How had I not found an opportunity to even bite or sting her?



``Wards, back off,'' she said.  ``Grace, Cuff, I want you out of sight, or Weaver bleeds.''



The two girls looked at me, and I nodded.  They backed away and stepped around the corners.



``Send your bugs away,'' she ordered me.



I started to open my mouth to protest, but she cut me off.  ``No tricks.  You have two seconds.''



Something about the fact that she was a known killer and her no-nonsense tone suggested she really was going to follow through.  I banished the bugs.



``The hell is she?'' Wanton muttered.



``She's a precog,'' I said, ``Something in that vein.''



The woman didn't respond.  The knife shifted locations, no longer touching my bare throat.



Was she distracted?  I controlled the insect-like limbs on my flight pack.  They were simple, weak, but they were also weapons.  The end of the claw stabbed for her face, for the general region of her right eye.



She turned her head, and it grazed harmlessly against her temple.  The blade of her knife turned around, and she caught it in the hinge of one mechanical arm.



I pulled away, but the knife being wedged in the gap of the joint gave her a measure of leverage over the mechanical arm.  She twisted it as though she were wrenching my arm behind my back.  The arm didn't give any, and I was forced to bend over a fraction.



Golem reached out from one wall, trying to seize her hair or neck, but she used me as a body shield, blocking the reaching hand.  Annex struck from below, attempting to ensnare her feet, but she threw me down into the reaching tendrils.  In the process, she got ahold of my wrist, twisting it much as she had the mechanical arm.



``Coordinate!'' I said, my voice tight.  I activated the thrusters on my flight pack in an attempt to tear way, but she wrenched me to one side, tilting my upper body while using one leg to block my lower body from following suit.  The end result was that the thruster only pushed me into the wall.  I managed to avoid slamming my head against the surface, but I was now pinned against a solid surface.  She still had my wrist behind my back.



\emph{Dodge this}, I thought.  I commanded my bugs to attack from every direction.



The Wards were taking my order seriously, attacking simultaneously.  Annex was looming, a spectre in the ground, raising up to try to engulf her, Golem was beside a wall, already reaching into it, and Tecton was kneeling, pressing his gauntlets against the ground.  Cuff and Grace had heard my order, and were stepping into view, advancing from behind the others.



The woman laid her free hand over the hand she was twisting behind my back.  Then she pressed my own fingers down into my palm, hard.



\emph{The control mechanism}, I thought.  Too late.  My bug was already moving towards the off switch when the thruster kicked in.  She swept my feet out from under me, and the thruster drove me into the ground.  The bug touched the off switch, but the impact had locked up the controls.



I hit Annex on my way down, buying the woman time to step back out of his reach.  The bug managed to turn off the thruster, but I was already sliding across the floor, right through the lower half of Wanton's telekinetic storm body and straight into Tecton's gauntlets.



The piledrivers fired into the ground a fraction of a second after I bumped into the gloves.  He'd likely aimed to place an effect directly beneath her, but my collision with the gloves had knocked his aim off by a fraction.  It was directed into a wall, creating a crack ten feet high.



The crack, in turn, summarily severed Golem's outstretched hand of granite.



The woman pulled her suit jacket off and held it out, sweeping it through the air to catch the thickest collection of my swarm within.  She folded it closed, simultaneously breaking into stride, heading right for Wanton.  Grace and Cuff were just behind him, with Tecton directly behind them, and Golem and I off to one side.  Annex was still pulling his spacial-distortion body together into something more useful.



``Stand down, Wards!'' I called out, before Wanton could make contact with her.  I was still pulling myself up off the ground.



The woman slowed her pace, coming to a stop.  Wanton materialized a few feet in front of her, swiftly backing away.  I dismissed the bugs that were closing in to attack.



``This goes any further, she's going to stop going easy on us and she'll murder someone, maybe murder \emph{all} of us,'' I said, not taking my eyes off her.  ``Because it's the only way she'd be able to stop the bugs from surrounding her, the only way to really stop Wanton once he closes the distance.''



She didn't speak.



``What the hell are you?'' I asked.  ``What's your power?''



She gave me a look, up and down, and then settled her eyes on mine.  Throughout the entire fight, she'd looked unconcerned.  She wasn't even breathing hard.  Except for a fleck of foam from the extinguisher here and there on the bottom of her pants leg and at the very end of her shirtsleeve, she wasn't even particularly \emph{dirty}.



She spoke, ``I win.''



``I gathered that much,'' I said.



``What I mean is that I can see the paths to victory.  I can carry them out without fail.''



I felt my heart skip a beat at that.  She'd volunteered an actual answer?



``The fuck?'' Grace asked.



``She's lying,'' Wanton said.  ``That's ridiculous.  It's not even close to fair.''



\emph{Powers aren't necessarily fair}, I thought.



``It doesn't matter,'' the woman said.  ``What matters is that there are \emph{other} enemies you should be fighting.''



``Enemies, \emph{plural}?'' I asked.



``We're approaching an endgame.  The end of the world, the sundering of the Protectorate.  Most of the major players know this, and the truce has effectively dissolved in every respect but the official one.  Those in positions of power are making plays.  Now.  Today.''



``And Alexandria showing up, that's a part of that?''  I asked.  ``Someone's ploy?''



``Yes.''



``Cauldron's or someone else's?''



``Yes,'' she said.  A noncommittal answer.



``And you're telling us this why?'' I asked.



``That should be obvious.''



``Okay,'' I said.  I wasn't sure it \emph{was} that obvious.  ``Just two questions, then.  Those people you just took-''



``Are gone,'' she said.



\emph{Gone}.  And there wasn't a thing I could do to change that.  I was almost certain I couldn't beat her, and I couldn't utilize whatever it was that was managing the portals to get access to them.  At most, I could survive long enough to report this to someone who could.



``Gone temporarily or gone permanently?'' Tecton asked.



``I don't expect anyone on this Earth will see them again, barring an exceptional success on our end.''



``You can't use your power to get those successes automatically, huh?'' I asked.



She didn't venture an answer.



``Right, that wasn't my second question.  What I want to know is why the hell you haven't used a power like yours to figure out how to beat the Endbringers.''



``My power is a form of precognition,'' she said.  ``Unlike most such powers, other precognitive abilities do not confuse it.  That said, there are certain individuals it does not work against, the Endbringers included.''



``Why?'' Tecton asked.



``No way to know for sure,'' she said, ``But we have theories.  The first is that they have a built-in immunity, something their origins granted them.''



``And the other theories?'' Golem ventured.  ``What's the next one?''



The woman didn't respond.



I suspected I knew what the answer was, but declined to speak of it.  It would do more harm than good.



``So you're blind here, useless,'' Grace said, a touch bitter.



The woman shook her head.  ``No.  I can consider a hypothetical scenario, and my power will provide the actions needed to resolve it.''



``And?''



``And we are doing just that,'' she said.  ``Doorway, please.''



She wasn't speaking to us.  Another gate opened behind her, and it wasn't to that sunny field with the tall grass.  There was only a hallway with white walls and white floors, a cool rush of air-conditioned air touching our faces.



``Doing just \emph{what}, exactly?''  Tecton called out after her.



She turned back to us, but she didn't respond.  The portal closed, top to bottom.



``Vehicles,'' I said, the instant she was gone.  ``I can sense some at the end of that path.  It's the fastest way back up that ramp.  Go, go!''



\blacksquare



Things had gotten worse in the thirty minutes we'd been gone.  Whole tracts of New Delhi had been leveled, and where the buildings had been tall and mostly intact while we collected the injured and met the `cold' India capes, only half of them stood even a story tall now.  The other half?  Utterly leveled.



It was a small grace that the fires had burned intensely enough that they'd exhausted the possible fuel, and the smoke was mostly gone, but that wasn't saying much.  I couldn't take a deep breath without feeling like I needed to cough.  Ozone and smoke were thick in the air, and the residual charge in the air was making my hair stand on end.



The Endbringer's path of destruction had continued more or less in one general direction, but beyond that, the damage was indiscriminate, indeterminate.  Behemoth's location, in contrast, was very clear.  A pillar of darkness extended from the ground to the sky.  Plumes of smoke and streaks of lightning slipped through the darkness on occasion.



The Chicago Wards rode bikes that were somewhere between a scooter and a motorcycle in design.  The vehicles might have been indistinguishable from normal road vehicles, but Tecton had quickly discovered that they had some other features.  There were gyros that allowed them to tilt without allowing them to fall, and the engines were electric, with only the \emph{option} of a generated sound, to appear normal.



Near-silent, the Wards zipped down the streets, zig-zagging past piles of rubble and fissures.   I flew above the group.



``Armband,'' I said, touching the button.  ``Status update.''



The ensuing reply was too distorted to make out.



Grue had gone ahead, though he'd no doubt had information on our whereabouts.  Bitch's dogs probably could have sniffed us out.  He'd gone ahead.  Why?



``Armband,'' I said, still holding the button, ``Repeat.''



I thought there might have been an improvement, as we got closer, but it was miniscule enough that I might have been imagining it.



I dropped down, settling on the back of Wanton's bike.  The wings were already tucked away, to minimize damage from the electromagnetic radiation, but I didn't want to push my luck further.



We passed a cluster of dead capes, alongside a series of massive gun turrets that had been mounted on hills and rooftops.  The heroes had made a stand here, or it had been one defensive line of many.  A number had died.



Had it been foolish to descend to the cold cape's undercity?  Should I have told them to take the wounded beneath, damn the consequences, so we could have helped more?



I hadn't thought it would take as long as it had, hadn't anticipated a fight with the woman in the suit.



I hoped I wouldn't regret this, that the absence hadn't cost our side something.  We weren't the most powerful capes in the world, but maybe we could have made a small difference here or there.



I'd \emph{learned} things, but did that count for anything in the \emph{now}, with tens, hundreds or thousands of individuals dying where they might have lived if we'd stayed?  Another lightning rod?  Something to slow him down and give them a precious extra second to form a defensive line?



The second defensive line, another collection of the dead.  Whatever method they'd tried here, there was no trace left now.



We were getting closer.



The third perimeter.  A giant robot, in ruins.  As many dead here as there had been at the last two points, all put together.



And just beyond this point, Behemoth, in the flesh.  He glowed white, marking the radioactive glow, and Grue's darkness wreathed him, containing it.  The ground beneath Behemoth was tinted gold, vaguely reflective, and geometric shapes were floating in the air, exploding violently when he came in contact with them.



With all of the obstacles he'd faced to this point, he looked less hurt than his younger brother had for his one-on-one fight with Armsmaster.  He didn't limp, or slouch, his limbs were intact, his capabilities undiminished.  The tears and rents in his flesh and the gaping wounds here and there didn't seem to have slowed him down in the slightest.



And with that, he managed to fight his way forward, out of Grue's darkness, striking out with bolts of lightning.  Forcefields went up to protect the defensive line, but only half of them withstood the intensity of the strikes.



``Armband,'' I said, and there was a note of horrified awe to my voice, ``Status update.''



The A.I.'s voice crackled, but Grue's darkness might have been suppressing the electrical charge, because it was intelligible.  ``\emph{Chevalier is out of action, Rime is present commanding cape for field duty. }\emph{Legend is out of commission. }\emph{Capes are to assist defensive lines and fall back when call is given.  Earliest possible Scion intervention is twenty-two point eight minutes from the present time, estimated Scion intervention is sixty-five minutes from present time, plus or minus eighteen minutes.}``



I clenched my jaw.  I'd committed to doing \emph{something}, but I had no idea what that could be.



I felt a sick feeling in my gut.



``Armband, status of Tattletale?''



``\emph{Out of commission.}``



By all rights, I should have reacted, cried out, declared something.  I only felt numb.  This was falling apart too quickly.



``Status of the other Undersiders?''



``\emph{Two injured.  Parian and Grue.''}



Which would be why Grue wasn't replenishing his darkness.  I closed my eyes for a second, trying to find my center, feeling so numb I wasn't sure it was possible.



Citrine's effect seemed to be maximizing the effects of Alexandria's attacks, because Behemoth wasn't able to channel them into the ground.



He swung his head in my general direction, and I could see the steel of Flechette's arrows in the ball of his eye, clustered.  Holes marked the point where the bolts had simply penetrated.



Other capes had managed varying degrees of damage.  The Y\`{a}ngb\v{a}n had formed a defensive squadron, using lasers to cut deep into Behemoth's wounds, and other capes clustered close to them, adding to the focused assault.



And yet he advanced.  Inevitable.



A blast of flame caught the defending capes off guard.  Their forcefields and walls of stone blocked the flame from reaching the capes, but did nothing to stop it from spreading as it set fire to nearby buildings, grass and the stumps of trees that had been freshly cut, if the sawdust was any indication.



As if alive, the fires reached forward, extended to nearby flammable surfaces, and cut off a formation.  They started to clear the way for retreat, and Behemoth punished them with a series of lightning strikes.



Golem was already acting, bringing stone hands up to block Behemoth's legs, two hands at a time.  Tecton moved forward, striking the earth with his piledrivers.  Fissures raced across the road, breaks to keep any impacts from reaching too far.



``Antlion pit!'' I shouted.



``Right!'' Tecton reported.



And my team was engaging, finding the roles they needed to play.  Grace, Cuff and I couldn't do much, but there were more wounded needing help getting out of the area.  Annex began reshaping the ground and walls to provide better cover.  Wanton cleared away debris from footpaths.



This particular front hinged on one cape, a foreign cape who was creating the exploding, airborne polygons.  I could see, now, how each explosion was serving to slow time in the area around the blast.  Had he actually been the inspiration for that particular bomb Bakuda had made?



Eidolon had added his own abilities to the fray.  He had adopted something similar to Alexandria's powerset, fighting in melee, ducking in only long enough to deliver a blow, then backing away before Behemoth's kill aura could roast him from the inside.  Eidolon was using another power as well, one I'd seen him deploy against Echidna.  A slowing bubble.



Cumulative effects.  Cumulative slowing.  Each explosion added to the effect, and Eidolon's slowing bubble was a general factor to help them along.  What did it really do if you tried to walk forward, and the upper half of your leg moved faster in time than the bottom half?  How much strain did that create?  Was there a point where the leg would simply sever?



If there was, Behemoth hadn't quite reached that point.  Either way, it seemed to be a factor in how slow Behemoth was moving.  He was getting bogged down.  Bogged down further as one foot dipped into Tecton's antlion pit.



Until the Endbringer struck out, targeting one group of capes with a series of lightning strikes so intense that I was momentarily left breathless.



And the explosive polygons disappeared.



He lurched forward, and even a direct hit from Alexandria wasn't quite enough to stop him.  The shockwave dissipated into the air, rather than the ground, and flying capes throughout the skies were driven back.



The Endbringer broke into a run, insofar as he could run, and nobody was quite in position to bar his way.  He ignored capes and struck out across the area behind them, hitting a building with two massive guns on it, a clearing, a rooftop with what looked like a tesla coil.  Fire, lightning, and concussive waves tore through the defensive measures before they could be called into effect.



\emph{We don't have the organization.  Our command structure is down}.  \emph{Tattletale is gone, either dead or too hurt to fight}.



He struck one area with lightning, and explosives detonated.  A massive forcefield went up a moment after they triggered, and the explosion was contained within, a cumulative effect that soared skyward.



For a solid twenty, thirty seconds, the sky was on fire, and the Endbringer tore through our defenses, making his way to a building with capes clustered on the roofs.  They weren't, at a glance, our offensive capes.  They were our thinkers, our tinkers, the ones our front line was supposed to be covering.



The woman in the suit had declined to share the \emph{other }reason her power wouldn't let her simply solve the Endbringer crisis.



The answer I'd declined to share with the other Wards was a simple one.  She had the ability to see the road to victory.  Maybe, when it came to the Endbringers, there was nothing for her to see.





