





Eidolon and Alexandria had settled into something of a rhythm.  Though his powerset was similar to Alexandria's on the surface, the eerie noises and the dimming of the light around the areas his punches landed suggested he was transmuting the kinetic energy of his punches into something else altogether.  Between Eidolon's strikes and Alexandria's, Behemoth couldn't quite adapt to the point where he was redirecting every strike, let alone the barrage of ranged attacks that the other capes in the area were directing his way.



The Endbringer staggered under the onslaught, but he was slowly adapting.  They'd managed to pin him for a minute, even costing him some ground by driving him back once or twice, but each successive minute saw him rolling with the punches more, advancing further when he found a second or two of mild reprieve.



His target: the command center.  Our flying capes weren't working fast enough to clear the entire rooftop, and every shaker we had -every cape capable of putting up a forcefield or creating a portal, raising a barrier- was busy trying to slow down the brute.  The Chicago Wards, or \emph{most} of the Chicago Wards were among them.



I tensed, but I couldn't move without exposing myself to one of the lances of electricity that were crashing down around us.  The capes on the rooftop were protected by an arrangement of tinker-made forcefields, it seemed, but those wouldn't hold.  \emph{Fuck}, hanging around on rooftops was dumb.  I'd learned my lesson on my first night out on costume, had avoided being put in that position since, excepting the fundraiser, where we'd been on the attack, and the time Defiant and Dragon had dragged me up to one, just a bit ago.



The guys up there were tinkers and thinkers.  They were our communications, supporting roles, strategists and healers.  A few of them were long-ranged capes.  Not really people who could hop or fly down five stories to the ground and walk away unscathed.  Not without help.



I waited and watched as Behemoth engaged the other capes, tracking what powers he was using and when.  He was presently staggering forward when he could, otherwise holding his ground, deflecting and redirecting attacks.  When he was free to do so, he reached out with his claws, and lightning lanced out to tear through the assembled capes.



Golem, to his credit, was going all out.  Hands of stone and metal rose from the ground to shield defending capes and balk Behemoth's progress.  I could make out Hoyden, leader or second in command of the Austin Wards.  She wasn't on the front lines, but was defending the mid-line capes.  It made sense with how her power worked, as her defensive powers provided more cover from attacks at greater ranges.  She threw herself in the way of lightning bolts and stood between Behemoth and the wounded.  When lightning struck her, detonations ripped out from the point of impact, seeming almost to short out the currents.



``Come on, come on,'' I muttered.



I could see Tecton creating fissures in the ground, no doubt intended to reduce the reach and effects of Behemoth's stomps.  Annex was creating bridges so heroes wouldn't fall into the gaps.



Dispatch, vice-captain of the Houston Protectorate team, zipped over to a group of wounded with accelerated speed, only to seem to \emph{pause}, as though he and his immediate surroundings were only video footage.  Color and space distorted violently in an irregular area around him as he hung there, just an inch over the ground, one hand at his belt and another reaching for someone with intense burns.



A half-second later, the effect dissipated, and they were all moving.  Dispatch was carrying one of the most wounded, gloves off and the sleeves of his costume pulled up, dried blood up to his elbows.  Others were bandaged and sutured.  His name, I knew, came from his ability to pick out targets in a fight, closing the distance to them and catching them in his temporal distortion effect.  He'd have minutes or hours, however long it took the air within the effect to run out, to end the fight with his super strength, durability and the close confines of the bubble.  To any observers, it appeared as though he'd won the fight in a heartbeat.  Apparently the idea extended to medical care.



Revel, leader of the Chicago Protectorate and official overseer of Tecton's Ward team, was stepping up to the plate.  Floating up to it, whatever.  She rose into the air, and caught one full current of lightning inside her lantern.  The sheer force of the blast knocked her back, and she struck a wall, pressed against it with her lantern held in front of her.



She began releasing spheres of light from the lantern, each larger than a human head, slow-moving but numerous.  Their trajectories were unpredictable, some striking friendlies, others carrying forward towards Behemoth.  Where they struck friendlies, they only exploded in brilliant showers of sparks.  When they touched Behemoth, they sheared right into him, cutting two or three feet deep before flickering out.



When she saw it was working, she only intensified the assault, spending the charge she'd accumulated to create fifty more orbs, before hurrying forward to intercept another stream of lightning that was flowing from Behemoth's claw-tip.  It was impossible to actually get in front before the lightning appeared, to save the lives that Behemoth was taking with the initial moments the lightning appeared, but she was stopping the lightning from flickering to the fourth, fifth or sixth target.



\emph{That} was what I was waiting for.  My limited experience with Endbringers had taught me one thing.  When someone actually found a way to respond, to cancel out the attacks or to deliver a measure of real damage, they changed tactics.



Some capes were already responding.  Captains and leaders were giving orders, and various barriers were being reinforced or thrown back up.  Some were trying to give the warning, but their voices disappeared in the midst of the chaos around us.



``Take cover!'' I hollered, and my swarm carried my voice.



It was only two or three seconds later, as the second wave of spheres drifted to Behemoth and began to cut into his torso and groin area, that he responded.  His `mouth' opened, the craggy spikes of obsidian `teeth' parting.



And he roared.  A sound that was slow at first, growing steadily more powerful.



Sound was a bitch of a thing.  It could be muffled, but blocking it entirely?  We didn't have Grue.



I fled, cranking my antigrav to `high' and risking unfolding my wings to use the propulsion systems as I made my way to for cover, putting as many buildings between Behemoth and I as I could.



My swarm responded to my call, assisting the capes who weren't fleeing fast enough.  They rose as a singular mass, a wall of tens of thousands, and absorbed the worst of the scream.  I wasn't sure it was enough.  Even with some distance and a dozen buildings between Behemoth and I, I had no defenses as it reached a crescendo.  My sense of balance went out the window, my very \emph{bones} hurt.



Closer to Behemoth, capes were bleeding from their ears, vomiting, passing out.  Organs and brains would be reduced to jelly as he continued.  My bugs weren't doing much to muffle the noise or soften the damage, if they were helping at all.



But my focus was on the rooftop.  I'd been waiting until he stopped using his lightning.  There was nothing saying he wouldn't use it \emph{now}.  He could use multiple attack forms at the same time.  Still, he was more focused on picking off the defending capes, the ones who were suppressing the noise.  Was Citrine among them?  I could see the golden glow of her power in the distance.



Director Tagg had given me an effective ranking of two for every single power classification.  Ostensibly, it had been because he hadn't wanted to underestimate me.  Was there a note of truth to that, though?  I wasn't sure about the `brute' or `mover' classifications, but did my power over bugs afford me a versatility that let me cover the bases on other fronts?



They still hadn't completely evacuated the roof.  The people who might have helped them down were disabled or otherwise occupied.  Getting them down was key, here.  The flying capes were more focused on assisting the capes near the front lines, helping the ones who could deal damage escape Behemoth's implacable advance and avoid the kill aura that accompanied him.



The roaring made it impossible to hear.  Even seeing was difficult, as my vision distorted and lost focus.  I very nearly tipped over, until I turned to my swarm sense.  Not perfect.  Even they were suffering, scattered and dying, at close range to the roar.  But it gave me an orientation, a plane to compare the tilt and angle of my body with.



I looped to one side to intercept some of my bugs, collecting the strands of silk they'd woven in one hand, then made my way around to the back of the building the heroes were clustered on.  Flying capes were settled on the ground, pausing to recuperate from the roar.  I took a second, myself, to get my bearings.  My back against the concrete, I could feel the \emph{building} shuddering in response to the roar.  But at least there was a small degree of reprieve, here.



When I'd caught my breath and reassured myself my insides hadn't been vibrated to pieces, I flew to the rooftop.  My bugs swept over the crowd.  No Tattletale that I could see.  No Accord, either, for that matter.



Two capes approached me, not quite Caucasian but lighter-skinned than the Indian capes.  One had a costume with a spiral to it, the other wore armor with tiny faces that looked like baby's heads.  Was he a villain?  They were rattling off something in French or Spanish as they reached out to take my hands.  Their eyes were wide with fear and alarm.



``I can't carry you!'' I shouted, raising my voice to be heard over the perpetual roar.  ``My flight pack isn't strong enough!''



They clutched at me, and one even pushed at another cape who'd gotten too close.



A little too much.  Too intense, here, too forceful.  \emph{I just want to find Tattletale.  I'll find a way to help you once I've done that}.



``Back off!'' I said, raising my voice.



The guy with the faces on his armor shouted so forcefully that spit flew from his mouth, as he pointed to the ground beyond the building.  He approached me, trying to hug himself tight to my body.  I pushed him away and backed up, trusting the antigrav to hold me aloft.



One of the capes on the rooftop approached me, pushing her way through the crowd.  She wore a golden mask with a woman's face, the mouth parted a fraction, with a black bodysuit.  It was softened a touch by the loose black cloth that draped down from her golden shoulderpads and breastplate.  The black didn't look so dramatic as it might have, mottled a brown-gray by the loose dust that had accumulated on it.



``Weaver,'' she said, her voice melodic.



``Arbiter,'' I responded.  One of Rime's underlings.  The one with the social danger sense, forcefield and sonic beam.  I supposed her forcefield wasn't quite large enough or versatile enough to offer a bridge down to the ground.  ``I've got other stuff I need to pay attention to.  Don't suppose you speak French?  Or Spanish?''



``Portuguese,'' she said.  ``And no, but give me a moment.''



She turned to the capes, but a heavy crash interrupted her before she could speak.



A building had fallen, toppling, and Behemoth hadn't done anything to precipitate it.  Nothing except the roaring.



Was that enough?  Was this building coming apart beneath us?



Where the hell was Tattletale?  My bugs flowed into cracks in the building, checking rooms only to find them empty.



``Hurry!'' I said.  I turned my attention to my swarm.  They extended out beneath me, forming into neat lines.  My bugs were slow to move through the structure.  I had to use the cracks that already existed in the walls, ducts and vents that just happened to be open.



``Speak to me,'' Arbiter said to the Portuguese capes.



The one with the spiral costume chattered out something I couldn't even guess at.  Arbiter nodded.  In very broken Portuguese, she asked a question.  The spiral man looked at the one with him, gesturing.



In less broken Portuguese, she spoke again.



That prompted another burst of explanation, or what I took to be exclamation.  They sounded desperate, afraid.



When she responded, she spoke just as quickly and flawlessly as the two native speakers.  She'd picked up the language in a matter of three exchanges.



I bit my tongue as the roar abruptly intensified, jarring me enough that my jaw was slammed shut.  It wasn't that he was roaring louder; one of the capes who'd been keeping the worst of the noise at bay had fallen.



\emph{Focus}.  My bugs extended lines of silk to the ground, while others held it aloft and kept it more or less straight, allowing the lengths to be carefully measured, the amount of slack controlled.



``Weaver!'' Arbiter said, raising her voice so I could hear her.



I turned around.



``I don't quite understand, there's a gap in translation, but he says he's pregnant with his dead teammates,'' she said.  Her voice cut through the noise, ``They're asking for him to be rescued next.''



\emph{Pregnant with dead teammates?}



Suddenly the little faces on his armor seemed twice as creepy.  I \emph{really} hoped that was a tragically bad translation.  Parahumans could be so fucked up sometimes.



``He gets rescued with everyone else,'' I said.  ``There's no way to prioritize.''



``Right,'' Arbiter said.



I secured the lines of silk on the roof's edge and on the ground.  I then pulled off a shoulderpad and retrieved the strip of silk that had held it in place.  I folded it over the cord and stepped over the edge, letting myself slide down the length of the cord.  Both ends were tied, and the slack was enough that it \emph{should} ease people to the ground.  I was okay with doing the test run, as my flight pack could handle the fall.



It didn't break.  Good.  Better than nothing.  I flew back to the rooftop, and I could feel the roar rattling me as I made my way up past the more solid cover.



``Should be fairly safe,'' I said, ``Silk cord got warm, from what my bugs are feeling, but I've got six arranged.  One person at a time, delay by about\ldots twenty seconds, at least, between trips, so the heat and friction doesn't wear through the silk.  It's not the strongest thread I've ever made.''



Arbiter glanced over the roof's edge.  I followed her gaze.  The silk was barely even visible.



``You're sure they'll hold?''



``No,'' I said.  I glanced over at Behemoth, ``But I'm less sure this building'll be standing in five minutes.  If a cape falls and dies, I'll take the blame.  Better than having everyone up here die.''



``You're not convincing me,'' she said, but she said something to the cape with the spirals on his costume.  With gestures and careful explanation, she got him to step up to the front, pulling his glove free of his fingers, using the excess fabric to slide down the silk line.



My bugs checked it after he'd passed.  Warm, but not so much that I was worried it'd split.



``Go!  Go!''  Arbiter said, grabbing the attention of the capes who'd been standing back and watching.



In seconds, we had capes sliding down the lines.  Arbiter was careful to keep them from overloading or applying too much friction too fast to the makeshift ziplines.



Behemoth had stopped his endless roaring.  He was using fire, now.  There was none of the uncanny precision the lightning had, but the fire moved with intelligence, spread easily, burned hotter than it should have, and it was virtually impossible to stop \emph{all} of it.  It slipped between force fields, between the fingers of Golem's stone hands, and it ignited any fabric and wood it touched, set grass alight.



I had to pull back my bugs.  I'd managed to keep the vast majority from dying, some fires and casualties from the roaring excepted, but this wasn't a place where they'd help.



Six more capes made their way down the line.  Arbiter used her forcefield to block some more agitated capes from making their way down before it was time.  She spoke in one of the local languages to the group.



``Thank you,'' I told her.  ``For helping keep this sane.  If it comes down to it, and the cords don't hold, I'll lend you my flight pack.  I can control it remotely.''



``Give it to someone else before you give it to me,'' she said, without looking at me.



``Right,'' I answered.  ``Listen, I'm--''



A cape gripped the cord for his turn, only to turn out to be far heavier than he looked.  Arbiter placed a forcefield under him, but it didn't do much more than slow his descent as he crashed through it.



Five cords remained, and there were too many capes here.



``\emph{Fuck},'' I said.



``He's okay,'' Arbiter observed.



But the others seemed more reticient now.



``What the hell is going on downstairs?  Are stairs too difficult?''



Arbiter shook her head.  ``Government building, it's set up to lock down in a crisis, which it did.  A rogue cape turned on the people inside, so the metal doors closed to protect others.  We've been reeling since.  Command structure's down, our battle lines collapsed--''



``You're talking about Chevalier.''



``Yes.''



``Then where's Tattletale?''



``I don't know who that is.''



``Teenage girl, dirty blond, costume of black and light purple.  She would've been with a short man wearing a suit.''



``I saw them.  They went downstairs with Chevalier.''



I could feel my heart in my throat.  ``Where are they now?''



``With other wounded.  We're relaying them a half-mile that way,'' Arbiter pointed.  ``Far enough away that Behemoth won't be endangering them anytime soon.''



Behemoth generated a shockwave, and one forcefield at the front of the roof flickered and died.  A tinker moved forward to try to restart it, and was struck down by a bolt of lightning before she could.



A wave of capes mustered the courage and slid down.  There were only eleven of us on the rooftop now, myself and Arbiter included.



I checked the lines, then cut one that was too frayed.  Four left.



``Four lines left,'' I reported, before someone reached for one that wasn't there.  My thoughts, though, were on Tattletale.  Injured or dead.



``Go,'' Arbiter said.  ``To your friend, your teammate, your partner, whatever she is to you, she's important.''



I shook my head.  ``You need me.  I can use my bugs to check the lines are okay.''



``There won't be any major difference if you're here or not.  Three more trips--''



A flying cape touched the rooftop only long enough to take hold of one of the people on top, then took off again.



``Maybe \emph{two }trips, and we're clear.  I'll go last.  \emph{Go}\emph{.}''



Another shockwave knocked out another forcefield panel.  A tinker was working on the generator, best as she could while hunkering down behind the sole remaining panel.  She said something frantic.  I couldn't understand her, whatever her language, but I could guess.  It wasn't her tech.



I hesitated, wanting to take the offer to escape.  Then I shook my head.  ``I'll stay.  Tattletale's important to me, but so is doing what I can here.  I can check the lines in a way nobody else here can.''



Arbiter only nodded, her eyes on the ongoing fight.



I drew up decoy-swarms, placing them across the rooftop, and stepped off the rooftop, hovering and using the building for cover.  Arbiter raised her forcefield to fill some of the gap in the tinker-created field, crouching in the crowd of swarm-people.  Others followed suit.  I covered them as much as I could without obscuring their vision.



Seconds passed before Arbiter gave the go-ahead.  Capes evacuated the rooftop.



Behemoth's lightning strike flashed through our ranks, right over Arbiter's squatter forcefield, through two decoys and striking a cape.



The crash of thunder seemed almost delayed, synced more to the cape going limp than the flash itself.  The body struck the roofop, dead before it touched ground.



Had the decoys spared two people from being hit, or was it chance that the bolt had made contact with them?  \emph{Fuck}.  Having more information would be \emph{key}, here.



Behemoth was continuing to suffer blows.  His progress had all but stalled, but he wasn't changing tactics.  Why?



Did he have a \emph{strategy}?  The Simurgh was supposed to be the tactician, Leviathan had the brute cunning.  Was Behemoth harboring a certain degree of intelligence?



I didn't like that idea, but I couldn't think of a good way to explain just why he was willing to stand there and take abuse.



Flying capes evacuated two more.  Arbiter gave the go-ahead for more to use the ziplines.



That left only the two of us here, and I had cover, at the least.



Lightning lanced past us, burning much of its initial charge on the forcefield.  It danced through the ranks of my decoy bugs.  Arbiter was left untouched.



``Damn,'' she muttered.  ``Damn, damn, damn.''



``Fuck waiting for heat to dissipate, just use the zipline,'' I said.  ``Hurry.  Second one, it's least worn, coolest.''



She half-crawled, half-ran to me.  I handed her the strap that I'd used for the test run, and she looped it over the line.



I followed her to the ground, my hand on the armor at her collar.  I probably didn't have the lift to keep her from falling, but I might have been able to soften the blow.



Not that it mattered.  The zipline remained intact, and she touched ground with a grunt.



I found Rime, casting wave after wave of crystals at Behemoth.  He was using shockwaves and fire to prematurely detonate or push away Revel's spheres, and Rime's attacks were suffering from a similar angle.



Rime was second in command, wasn't she?  Or was it Prism?



Rime would be more receptive to listening, either way.  I used my bugs to speak to her.  ``\emph{Command center evacuated.  Can relax front line if you need to}.''



She didn't respond to me, but I could make out her orders as she shouted the words, ``Fall back!  Stagger the retreat!''



I exhaled slowly.



``You've done your duty.  Go to your friend.  Figure out what's going on,'' Arbiter said.



I nodded and took off.



Through my bugs, I spoke to Tecton, ``\emph{Back shortly.}''



He mumbled something I couldn't make out.  It might have been `okay'.



As I got more distance, I felt safe to withdraw the wings again.  I picked up in speed, putting Behemoth and the fighting behind me.



I found a temple with wounded inside.  The exterior was opulent, the interior doubly so.  Now it was a triage area.  There were more burns here, crushed limbs, people coughing violently.  It wasn't damage suffered from direct confrontation with Behemoth.  It was secondary damage, taken from the fires and smoke of burning buildings.



And inside one curtained area, there were the wounded capes.  I approached, folding the wings away and moving forward with antigrav and the occasional touch of foot against ground to propel myself forward further.



I stopped by Tattletale's bedside.  I'd found her within instants of the temple falling in my range.  Her lips moved as she recognized me, but no sound came out.  My eyes moved to the tube sticking out of her throat.



``You really gotta stop doing this,'' I said.



She only grinned.  She reached over to the bedside table and retrieved a pen and notepad.  Her grin fell from her face as she wrote something, then tore the page free, handing it to me.



he's going easy on us.  all Endbringers are.  but Behemoth holding back, even from moment he arrive.  taking more hits than he should.



``We already knew that they're holding back for some reason,'' I said.  ``The way they space out attacks, they could accelerate the timetable or coordinate their strikes if they wanted to fuck us over.''



Another note:



they want to lose I think.  set themselves up to fail.  but not fail so bad they risk dying.  levi was after something, noelle I think.  but why didn't he show up closer to downtown?



``I don't know,'' I said.  I felt a little chilled at the idea that \emph{this }was the Endbringers pulling their punches.



big b wants something.  not at india gate.  somewhere past it.  why not come up right underneath it?



``I don't know,'' I repeated myself.  ``\emph{It doesn't matter}.''



matters.  looked at past attacks.  pattern.  small pattern.  behe attacks nuclear reactor, appears some distance away.  attacks birdcage, appears in rockies, no sign he was close or beneath cage.  pattern says he wouldn't emerge this close if he just wanted to attack india gate.  He attacking something north of it.



``Just tell me, is there anything \emph{I }can do?''



I was trying to find his target.  accord was trying to find way to stop him, coordinate counteroffense.  accord dead, I useless.  get me computer?  maybe I can help still.  Ppl here not helping.  scared of me.



Accord was dead?  What did that spell for the Undersider-Ambassador alliance?



No.  I couldn't let myself get distracted.  There were more immediate concerns.



``Computers are probably down,'' I said.  ``I think there's too much electromagnetic energy, no cell towers, no radio, no internet.  Armbands aren't working, and I'd expect them to be the last thing to stop working.''



She spent an inordinate amount of time writing the next message.



I shifted my weight from one foot to the other while I waited for her to finish, then accepted the note and read it.



FUCK



Each letter had been traced over several times, and the entire thing had been underlined twice.



I glanced at her, and she was scowling, already writing the next message.



``I'll see what I can do,'' I said.  ``You're a distance away from the fighting, maybe a phone works.''



But she was already handing me the next piece of paper.



you go.  find it.  find his objective.



``There's other capes better for that than me.''



get help then.  but you can use swarm.  search.  we win this by denying him his target.



I frowned, but I didn't refuse her.  I started to leave, then hesitated, turning back to her.  I opened my mouth to speak, then saw the note.



go already.  I ok.  I get healer another day.  not worried.



And I was gone, flying over the heads of the wounded as I made my way to the front door.



The availability of healing made for an interesting, if ugly, dynamic.  Capes like Tattletale, capes like \emph{me} could be reckless, we'd get our faces slashed open, our backs broken, our throats severed, blinded and burned, and we'd get mended back to a near-pristine condition.  Tattletale still had faint scars at the corners of her mouth, regenerated by Brian after his second trigger event, but she'd mended almost to full.  I'd had injuries of a much more life-altering scale undone by Panacea and Scapegoat.



If we died, we were dead, no question, unless I gave consideration to Alexandria's apparent resurrection.  But an injury, no matter how grave?  That was something that could be remedied, it lent a feeling of invulnerability, an \emph{image} of invulnerability.  So we continued being reckless, and we would continue to be reckless until something finally killed us off.



Was there a way to break that pattern?  Could I afford to?  My ability to throw myself headlong into a dangerous situation was part of the reason for my success.



I looped back towards the main confrontation, finding the thinkers I'd helped off the rooftop.  Some were moving to assist allies, others were fleeing.  One pocket, at a glance, seemed to be trying to form a second command center.



I moved towards the cluster of them.



Two Indian capes, one Caucasian.



``English?'' I asked.



``Yes,'' the Caucasian said.  ``Just me.''



``Trying to enlist help.  Names and powers?''



``Kismet, balance thinker,'' the Caucasian said.  He wore a white robe with a hard, faceless mask that had only slits for the eyes.



``And the other two?''



``As far as I can tell, Fathom and Particulate.  Best translations I can give.  My Punjabi isn't strong.''



``Their powers?'' I asked, with a restrained patience.



``Displaces people or things to another dimension, filled with water, brings them back.  Particulate's a dust tinker.''



What the fuck is a dust tinker?  Or a balance thinker, for that matter?



``Okay, I'm going to find others,'' I said.



``Wait, what's the project?''



``A mission.  Finding whatever it is that Behemoth wants.''



``We've got others on that already.''



``Nobody's reported back,'' I said, ``Or at least, nobody's formed a defensive line or put safeguards in place.''



``You're sure he's after something?  They've attacked cities just to kill people before, and this is a dense population center.''



``He's after something,'' I said\emph{. }``He's got a direction, and a friend told me he's targeting a point beyond where the heroes are searching.''



``We'll help look,'' he said. He rattled off a few lines of Punjabi to the capes in his company.  One of them, Particulate, I took it, removed what looked like a fat smart phone from one pocket.  He peered at it.  Some sort of scanning instrument.



``Hey, either of you have a phone?''  I asked.



Kismet nodded, then handed me the phone.



``Can I keep it?''  I asked.  ``I can get it back to you later, probably.''



He made an exasperated noise.  ``I thought you wanted to make a call, not keep it.''



``It'd be for a good cause,'' I promised.



He sighed, ``Take it, then.''



I wound silk around it and then had bugs carry it off in Tattletale's direction.



``You think it's a cache of nuclear weapons, or what?''  Kismet asked me.



``I don't know,'' I said.  ``Go look, towards India Gate.  I'm going to round up others.''



``On it,'' he said, before speaking another line of Punjabi.  ``And kid?''



I hesitated in mid-air.



``Thanks, for the escape route from that rooftop.''



I didn't respond, taking off.  Rude, maybe, but taking the time to respond was stupid, when there was this much going on.  Making me wait while he thanked me was similarly dumb.



I waited until the phone reached Tattletale's hands, then drew closer to the fighting, and the capes who were closer to the battlefront.  When Rime was in my power's reach, I contacted her.



``\emph{Tattletale thinks she has a lead on Behemoth's objective.  Mobilizing thinkers to find it.}``



I was nearly drowned out by the chaos of the fighting.  Behemoth was standing partially inside a building, and it was blazing, pieces of it falling down with every heavy impact the heroes delivered.



``Say again,'' she said.



I repeated myself, speaking the words aloud under my breath, to gauge the proper way to form the sounds with my swarm.



``Good,'' she said.  And that was all.  She was fighting again, trying to freeze the building so Behemoth was encased.



I found two more thinkers and gave them directions.  We'd search the area beyond the Rajpath.



Behemoth generated a shockwave, and I could \emph{sense} the heroes reacting to it.  The only cover here was cover heroes like Golem were creating, and the concussive shock traveled through the air, knocking capes off their feet or out of the air.



I grit my teeth and pressed my back to a building as it rolled past me, fell over at the impact.



The Endbringer strode forward, using the momentary break in the attack to cover more ground.  Unfortunate capes who'd been pushing their luck were left trying to run for cover, only to be caught within his kill aura.



Rachel rescued one or two, though the heroes might have debated the nature of the rescue.  Her dogs seized people in their mouths, running, dropping them at a safe distance, before moving in to retrieve more people.  Some of the rescued individuals were left slowly climbing to their feet, no doubt bruised from the dog's teeth and dripping with drool.



One dog, a person in its mouth, was struck by a bolt of lightning.  It fell, sprawling, then slowly climbed to its feet.  I could tell with my bugs, that the person in its mouth was no longer alive.  Still, it dutifully carried the body to safety and deposited it on the ground, before limping back towards the battle.



I belatedly remembered to pay attention to my team.  Tecton was busy erecting barriers, raising the earth in shelves with his piledrivers. Annex was reinforcing everything, fixing other people's work, providing loose cover for ranged heroes to hide behind, and delaying collapses.  Powerful.



Grace, using her strength to carry the wounded.  Wanton was venturing into more dangerous ground with the safety of his telekinetic body, returning to human form to help the wounded and trapped, then retreating with the same form, moving on to the next person.  Cuff was helping a tinker.



Golem was forming barriers, limiting the movements of Behemoth's legs, and shoring up the building the Endbringer was wading through.



The constructions weren't doing enough.  We needed to change tactics now that this wasn't working, sort of like the Endbringers did.  If not constructions, then maybe \emph{de}structions.



``\emph{Tecton, pits.  Have Annex cover them},'' I ordered.  ``\emph{Think controlled collapses.}''



I couldn't make out his response.  I hoped that didn't mean he couldn't make out \emph{my} statements.



``\emph{You're in charge until I get back.  I have other orders,}'' I added.



I returned to collecting thinkers and other stray capes, taking only a minute before heading for our destination.



There were heroes and PRT officials at India Gate, and lined up across the Rajpath.  A handful of thinkers and tinkers were here.  Not ones I'd sent, but official ones, directed to scan and search for whatever Behemoth might be after.



``\emph{Search north,}'' I communicated, sending moths and butterflies to pass on the message.  I didn't wait to see if they'd listen.  I kept moving.



I zig-zagged across the landscape, scanning every surface with my bugs, as the fighting continued in the distance.  Behemoth wasn't quite visible from this vantage point, but the cloud of smoke and the lightning suggested it wouldn't be long.



How many capes had he killed?  How many more would die?



I crossed paths with Particulate, who had apparently been filled in by Kismet.  He handed me one of the scanning devices, and I took off.



\emph{Damn tinkers}.  Their stuff was making life so complicated, now.  Too many things to keep track of.  Antigrav, propulsion, sensing things with my bugs, paying \emph{attention} to what I was sensing with my bugs, coordinating people, with sectors for them to cover, and now tracking the stuff with the scanner.



Not that it was impossible.  I was managing everything but the bugspeak without a problem.



The scanner showed me only gibberish at first, with sixteen bars divided into eight individual pieces, each of which could be any number of colors.  Each rose and fell as I moved and as I turned the scanner.  Moving past Particulate, I noted that the rise and fall of the bars was linked to my relation to his scanner.



We were triangulating.  Or did we not have a third?  Kismet was somewhere out of my range, at present, as was Fathom, so I couldn't be sure.



The bars rose as I pointed in Behemoth's direction, a mix of blues, greens, yellows and reds.  Was it tracking energy?



I turned away, and found another bump, almost all \emph{white, }the rest yellow.  Nothing tracked in any significant quantity at Behemoth's location.



It was something.  I circled around until the bars reached a peak, every single one of them topping the charts.



Nothing.  I used my power, but I couldn't find anything more complex than a desktop computer.



Then it adjusted.  The bars each dropped until they were only four or five high.



Was Particulate doing something on his end?



It dawned on me, as I tried to narrow down our target, that this was \emph{big}.  Something that topped the basic readings just by being within a mile of it.



And I found it.  My bugs could sense an underground chamber.  Concrete walls, impenetrable to earthworms, and no obvious entrance.  I looped back to communicate to the others.  The English-speakers, anyways.



Then, as the faster and the closer thinkers caught up with me, I approached the site.



Particulate and Kismet joined me.



This underground chamber was different from the one I'd seen closer to Behemoth.  There was no ramp leading up, nothing to suggest an elevator.



``Not sure how to get through,'' I said.



``Smart of them,'' Kismet said.



``I know, but it doesn't help us.''



Kismet said something to Particulate, and the tinker drew a gun from a holster with an excess of care.



Then he fired.  There was no beam, no projectile.  There was only a corridor, three feet across, carved into the earth, and \emph{plumes }of dust.



We backed away, Kismet coughing as he caught some of it.  Particulate, a tinker with a narrow, overlong bald head, said something in his language, almost musical, humorous.  He glanced at me, his eyes covered by goggles, his mouth covered by a fabric that hugged every wrinkle of his lower face, as though it were a micron thick, and smiled.  I could see the contours of his teeth and gums behind the strange fabric.



``Battery,'' Kismet said, stopping to cough, ``is dead.  Three shots.  Tried two on Behemoth, didn't work.  He likes that it was useful.''



``Damn,'' I said.  If they \emph{had }worked\ldots



I didn't waste any more time.  I handed them a length of cord, then disappeared down the hole.  My feet skidded on the smooth, almost glassy surface, but my flight pack gave me some lift.



Now that I was lower, I was free to feel out the surroundings, and mentally map out the entire complex.  It took time, but the others were slow to descend to the lower corridor.



Was there a whole \emph{undercity} beneath New Delhi?  Some kind of subterranean realm of corridors and rooms, large and small?  Did the good and bad `cold' capes accidentally dig into each other's corridors at any point?  Collapse sections of each other's undercity?



Geez, it wasn't like the city wasn't large enough already.



I was drawing a mental picture as my bugs spread out.  There were people here, but they weren't doing anything special.  Sleeping, cooking, fucking, smoking some sort of pipes\ldots no.



And in the midst of it, as Particulate adjusted his tracking device to further narrow the sensitivity, we closed in on a void.  A part of the underground chamber my bugs couldn't touch.



Particulate said something, arching his eyebrows as he looked down at the scanner.



``A lot of energy,'' Kismet translated.



``How much is a lot?'' I asked.



Particulate spoke without Kismet translating for him.



``More than Behemoth has given off during his entire stay in New Delhi,'' Kismet said.



I stared at the little scanner and the white bars.  ``There's no way in, as far as I can tell.''



``There wasn't a way into this base either,'' Kismet said.  ``Maybe they have a way to enter and leave.''



``Okay,'' I said.  ``We know where Behemoth's target is, even if we don't know \emph{what} it is.  Let's retreat, communicate with--''



But Particulate was already moving, tampering with the gun that had created the corridor.



``Stop him!'' I said.



Kismet reached over, but Particulate was already tossing the gun to the point where the floor met the wall.



It started flashing rapidly, increasingly bright, and Particulate bolted.  It was almost comical, as though he'd been taught to run by a textbook.  His hands were out flat at his sides, his arms and legs bent at rigid right angles as he sprinted away, almost robotic in the movements.  He shouted something in Punjabi.



\emph{Almost} comical.  When you saw a bomb disposal team running, as the joke went, you ran to keep up.  The same applied to any tinker and a device that flashed like that.  Kismet and I ran after him.



The gun exploded, silently, without fire or light or electricity.  There was only a roughly spherical opening carved into the area.  It was wide enough to lead into the tunnel above and below us, and had sheared through the five or six feet of solid earth that separated each floor.  At the far end, I could see where it had cut into a corner of the previously inaccessible room.



We approached, and I could see a cape inside, or a parahuman, if `cape' applied.  He was disheveled, with dark circles under his eyes, his skin pale, his beard and hair bedraggled.  His clothing, by contrast, was opulent, clean: a rich indigo robe, a sapphire set in a gold chain, a gold chain for a belt, and a golden sash.



And above him, the energy.  There were two golden discs, and something almost \emph{alive} seemed to crackle between them.



``It's \emph{Phir S\textoverline{e}},'' Kismet said, backing away.



``The glowing thing in the air or the person?''  I asked.



``The person.''



``Who's Phir See?''  I asked.



``\emph{S\textoverline{e}.  }He's one of the reasons the American girl's PRT can exist,'' Kismet said.  ``When they talk about disbanding it, the PRT only reminds them that monsters like this lurk elsewhere.''



The man slowly turned to face us.  He wasn't an \emph{old} man, but he moved like one.



``Monsters?''  I asked.  ``I've fought monsters.  Just tell me what kind of monster he is.''



``The kind that is too smart for \emph{all} of our good,'' Kismet said.  He'd frozen the moment the man set eyes on him.



\emph{Phir S\textoverline{e}} spoke\emph{, }``That is compliment?  Yes?''



``Yes,'' Kismet said.



``Then I thank you.  Girl?  I recognize you from American television.''



``I go by Weaver, now.''



``I do remember.  You had much power.  You turned it down.''



``It wasn't for me,'' I said.



``You are more comfortable where you are now?'' he asked.



``Now as in here, in this fight, or as a hero?''



``Either.  Both,'' he stated.



``Honestly?  No on both counts.  I'm still figuring it out.''



He inclined his head.  ``This is to be respected.  Making hard choice.  The challenge of the young adult.  To find identity.''



``Thank you,'' I said, still wary.  Everything about Kismet's reaction was telling me this guy was to be feared, so I had to step carefully.  ``Can I ask what that thing is?''



``A weapon,'' he said.  ``A\ldots how do you Americans say it?  Time bomb?  Only this is joke.''



``He makes portals,'' Kismet said.  ``Using them, he can send things back in time.  Something goes in portal B, comes out of portal A a few minutes earlier.  Or the other way around.''



``Or, as I discover, I make loop,'' \emph{Phir S\textoverline{e}}said.  ``Weaponize.  Simple light, captured in one moment, redoubled many times over.  I move gate, and that light will pour forth and\emph{ clean}.''



I could remember what Particulate had said.  \emph{More energy than Behemoth had created since arriving in this city}.  Only this would be directed at a single target.



``Clean isn't the word you want,'' I said. ``Scour?''



``Scour,'' \emph{Phir S\textoverline{e}} said, he inclined his head again.  ``I thank you.''



``Behemoth wants his hands on it,'' I said.  ``On that energy.''



``I want this on Behemoth.  Do great harm.  Even kill.''



``Shit,'' Kismet said.  He backed away a step.  ``This is--''



``Stay,'' \emph{Phir S\textoverline{e}} said.  His voice was quiet, but it was clear he expected to be heeded.



Kismet glanced up at the glow, then turned to run.



He wasn't even turned all the way around when there was a flicker.  A man appeared just in front of Kismet.  A teleporter.



And his forearm extended through Kismet's chest.



Then he flickered, like a bad lightbulb, and he was gone, leaving only a gaping hole where the arm had been.  Kismet collapsed, dead.



\emph{A teleporter who can bypass the Manton effect}.



``Stay,'' \emph{Phir S\textoverline{e}} told us, again.  He hadn't even flinched, but the space between his bushy eyebrows furrowed as he stared down at Kismet.



My heart thudded in my throat as I glanced down at the body.



Particulate said something, spitting the word.



\emph{Phir S\textoverline{e}} said something in Punjabi, then turned to me, ``Is rude, to speak in language you cannot understand.  He call me evil, so I not speak to him further.  But you understand, do you not?  You know what form this war take?  The danger we all face, from monsters like that, from others?''



``I don't think many top the Endbringers,'' I said.



``Maybe not so.  Maybe.  But you have tried being cold.  Killing the enemy, yes?  Because ruthless is only way to win this war.''



``I met some people.  I think they were your adversaries,'' I said.  ``Glowing eyes?  Reflective?  Like mirrors?''



``Yes.  Enemy.  They petty evils that walk this city.  Organize crime.  Slave, prostitute, murder, mercenary.  My side, we root out corrupt.  Ruthless.  Government prefer them to us.  Paint us as evil, pay them to carry on.  But you know what this is like, yes?''



``More or less,'' I said, not breaking eye contact.  ``And those guys, they're ruthless in the same way you described, I guess?''



``More, less,'' he said, as if he were trying on the phrase, ``Yes.''



``You want to hit Behemoth with this\ldots time bomb,'' I said.  ``But\ldots I think that's what \emph{he} wants.  He's holding back.  My thinker friend, she said so.  He's taking more hits than he should, and I'm just now realizing he might be doing it because he wants to be ready for when you hit him with \emph{this}.  He'll push it out into the ground, or into the air.''



``Yes.  This is likely,'' \emph{Phir S\textoverline{e}}said.  ``This is what he may want.  I hoped for the Second or Third.  This will have to do.''



``They've tried this stuff before,'' I said.  ``Nukes, gigantic railguns, tricks with teleportation and portals.  It doesn't work.  You won't do anything except get a lot of people killed as collateral damage.''



``We time this.  Strategic,'' \emph{Phir S\textoverline{e}}\emph{ }said, calm, as if he were talking to a panicked animal.  ``Come.  Step in.''



\emph{Right,} I thought.  \emph{Approach the temporal bomb}.



But I did.  No use ticking off the guy with the murder-teleporter on call.  Particulate followed me as I navigated the way to the room's interior.



There were television screens all across the wall.  Five showed the ongoing destruction from distant cameras.  Two showed grainy camera footage.  The last showed what looked to be an Indian soap opera.



``Thirsty,'' \emph{Phir S\textoverline{e} }commented.



The teleporter flickered into existence, then disappeared.  \emph{Phir S\textoverline{e} }had a bottle of water in his hands that he hadn't held before.  He turned our way, bushy eyebrows raised as a faint smile touched his face.  ``Might I offer you anything?''



I shook my head.  My stomach was a knot, my heart was pounding.



Particulate said something, but \emph{Phir S\textoverline{e} }ignored him.



``We watch the First,'' \emph{Phir S\textoverline{e} }said.  ``He let his guard down, I strike.''



``I've seen an Endbringer fool another brilliant man who thought he had a surefire way to win,'' I said.  ``They're cleverer than we think.  What if Behemoth fools you?''



``Then New Delhi pay for my mistake,'' \emph{Phir S\textoverline{e} }answered me.  ``I have daughter there.  She join bright heroes, popular ones.  She pay for my mistake, if she still lives.  I live, down here, spend life mourning.''



He looked genuinely upset at the idea.



``You want to win?'' I asked.  ``You take that thing, aim it for the sky.  Deplete it, so Behemoth's entire goal for coming here is gone.''



``Is a chance,'' \emph{Phir S\textoverline{e} }told me.  ``To strike them harder than anything yet.  You tell me, is that not worth it?''



``Worth risking this city?  Your daughter?  The lives of the heroes here?''



``Yes.  Is worth.''



``No,'' I retorted.



He looked at me, and I could read the unhappiness in his expression.  Not a condemnation or even him being upset with me.  Disappointment in general.



\emph{The woman in the suit told me there were people with their own agendas.  Monsters.  This is one of them, and he thinks we're kindred spirits}.



``I tell you because you are ruthless, Weaver.  Do not stop me,'' he said.  ``I die, focus waver, time bomb explode.  Aimless, no direction.''



``Indiscriminate,'' I supplied a better word.



``Indiscriminate,'' \emph{Phir S\textoverline{e} echoed me.  ``}India gone.  You die, even down here.''



I raised my head, staring up at the two golden discs and the current that seemed to run between them.  I would have thought it would be brighter.



``Hero fall.  We wait,'' he said.  ``When fight cannot be won, I \emph{strike}.''



I tensed as I watched the fighting on the screens.  They flickered intermittently in a delayed reaction to Behemoth's lightning strikes.



``Very soon,'' he said, his eyes fixed on the monitor.  ``You \emph{stay}.''





