





Particulate said something, and the amount of \emph{invective} in his tone was enough to make it clear, even if I couldn't understand the language.



Phir S\textoverline{e}\emph{ }said something in response, his voice calm, almost as though he were talking to a child, then took another drink of his water.  His eyes didn't leave the screens.



Behemoth had nearly reached India Gate.  The defense continued to be staggered.  One to four parahumans working together to slow him, to impede his progress and buy time for the others to wear him down.  When they failed, the measures circumvented or the capes in question killed, he advanced, the heroes retreated as best as they were able, and they enacted the next counteroffensive.



But each time they fought, he did damage.  Capes perished, tinker devices were turned into lumps of hot metal.  Each time the capes mounted a defense, the defense was weaker.



``Something is wrong,'' Phir S\textoverline{e} said.



``Chevalier was attacked,'' I answered.  ``They were planning a coordinated defense, I think, but someone beheaded our group at the worst possible time.''



``I see.''



``I'm not going to ask any questions about how you guys operate, but it's obvious you're organized.''



``Careful,'' Phir S\textoverline{e} told me.  He didn't even look at me.  The defensive line was using Clockblocker, now.  They'd erected a loose grid of wires, almost invisible, but for the flashing lights set at regular intervals.  Alexandria and Eidolon were trying to hammer the Endbringer into the barricade.



``You've got secrets to protect.  Fine.  Cool.  I'm not going to pry.  But maybe we've walked similar paths.  We had similar practices, probably.''



He cast me a momentary glance over his shoulder, meeting my eyes for a second before he turned back to the screens.  An acknowledgement, without accepting or denying my point.



``My old team wasn't nearly as effective as you guys seem to be.  But we operated in secret, we understood some key elements.  The need for information, having to know when to go on the offense, being unpredictable against enemies who are already expecting you to try and catch them off guard.''



``Talk slower, please,'' Phir S\textoverline{e} told me.  ``My English is not strong, and I am very tired.''



He looked like he might drop any minute, like he'd barely eaten, hadn't slept\ldots



``How long has it been since you slept?''  I asked.



``Three days.  We thought an Endbringer would attack soon, so I prepared, to be ready when the time came.  Too early, I had to stop, restart.  This time, he came, but I am weary.  The talking, is good.  Distracting without being dangerous.  Continue, please.''



\emph{What happens if he nods off?}  I wondered, looking at the `time bomb'.  The same thing he'd stated would happen if he were killed or knocked out?



``Okay,'' I answered.  I took a second to compose my thoughts.  ``You mentioned how you have to be hard, heavy handed if you're going to succeed in a situation where your enemies are as scary as the people you and I have gone up against.''



``Yes.  Heavy handed.  Like the judge's hammer\ldots''



``Gavel,'' I supplied.



``The gavel.  Harsh justice.  Crush the enemies who cannot be converted to your side or convinced to do otherwise.''



``Yes,'' I said.  I thought for a second, then made my argument.  ``And you know the power of having all of the information.  The power of having a group that can \emph{communicate} that information.  Communication is key, and a group that doesn't even need to communicate because they function so well together is better yet.''



``You had this.''



\emph{With the}\emph{Undersiders.  }``We were close.  And losing that, it's scary.  Maybe the least fun part about being a hero.  But you understand?  You agree, about information and communication?''



He didn't respond, as he watched the screen.  \emph{Is he going to nod off right here?}



On the monitors, a successful hit on Eidolon's part struck Behemoth into the grid of wires.  It had taken time for the Endbringer to approach the wires, set safely outside of his kill range, and some were already coming free of Clockblocker's power.  Still, they sank deep, cutting a diamond-shaped pattern into his hide, shoulder to heel.  Alexandria charged, trying to drive it home, and Behemoth struck out with one claw, a swipe.



He must have captured all of her forward momentum and motive impact and redirected it at her, because he didn't move an inch in response to the hit, and she crashed into the ground at a shallow diagonal angle.  Her body carved a trench a few hundred feet long, judging by the cloud of dust that rose in her wake.



Behemoth lurched forward, and the grid of wires cut him again on their way out.  Chunks of flesh were carved free.



The Endbringer clapped his hands together, and forcefields went down, defenses and defending capes falling in response to the impact.



Clockblocker's grid of wires dropped out of the sky, blinking white lights falling like sparks from a large firework.  I suspected that I knew what it meant.



Shit.  I hoped he was okay.  Clockblocker wasn't a bad guy, as heroes went.



``I agree,'' Phir S\textoverline{e} told me, belatedly.  ``And I think I see what you are going to say.''



``Let's \emph{communicate} with them.  With everyone.  Half the screwed up crap I've seen, it's been because we're fighting between ourselves.  The best achievements, the truly heroic stuff I've seen?  It's been when we worked together.  So let's maximize our chances.''



``You have been doing this how long?  A year?''



``Months.''



``I have been doing this for ten years.  I admire you for retaining your\ldots'' he trailed off.



``Idealism?''



``Not a word I'm familiar with, Weaver.  Faith?''



``Faith works.''



``I have none left, after ten years.  No faith.  We are a wretched, petty species, and we have been given power to destroy ourselves with.''



``Ironic, given what you're trying to do here.  You're going to kill people, kill bystanders, on a gamble.''



Phir S\textoverline{e} peered at me.  ``What chances would you give this gamble?''



``One in three?''



His stare was cold as he met my eyes.  ``One in three.  That is\ldots perhaps unfair.  No matter.  If I'm wrong, we lose this city.  If I'm right, we kill Behemoth.  I would take those odds, Weaver.  I would take them, I would watch this city be wiped from the earth, knowing that people I am fond of would die.  I live in a civilian guise most days, waiting until I have a task from those more powerful than I.  I would perhaps be killing the butcher I talk to every day when I walk to the store for food.  I would kill the widow who lives next door to me, her child, if they have not evacuated.  I have mentioned my daughter, much like you in her abundance of faith in people.''



``I wouldn't exactly call myself an idealist to that extent,'' I said.  I paused.  ``Phir S\textoverline{e}-''



We'd started talking at the same time.  He talked over me, half of his attention on the screens.  ``I will take this gamble and perhaps kill those people in the process.  I will kill those people who can make me smile and feel more human than I am, I will grieve their deaths, and then I will take that gamble again.  Because one city, however grand, is worth that chance.''



I thought of doing that, of rolling the dice like that, with my father, with the people in my territory.  ``Easier to say than do.''



``I have done it, Weaver,'' Phir S\textoverline{e} told me.  ``My wife, my sons, years ago.  A similar problem on a smaller scale.  I can walk through minutes, I could have walked back to save them, but I let them die because it meant a monster would remain gone.  What merit is a gamble, a sacrifice, if you stake things that matter nothing to you?''



I stared at him.  He was young, no older than thirty-five, but the lines of his face, the slumped posture, the slowness with which he moved\ldots they spoke of a horrendous exhaustion.



I didn't have a response for Phir S\textoverline{e}'s question.  He smiled a little, and turned back to the screens.



Behemoth was roaring, a sound that didn't reach us underground.  With the monitors on mute, it didn't translate there either.  Still, the images vibrated, the flickering intensified, and the defenses the heroes had established were crumbling.  India Gate was damaged, an incidental casualty of the fight more than a target.



My bugs sensed motion to my left.  I glanced at Particulate, and saw him holding his scanner behind his back.



It was pointed at Phir S\textoverline{e}'s `time bomb'.



His other hand was drawing a slender gun from a pocket in his combination lab coat and jacket, a gun like something from retro science fiction, with no barrel.  There was only a small extension on the end, much like a satellite dish.



Another disintegration gun?



He saw me looking, glanced at Phir S\textoverline{e}, who had his back turned, then looked back at me.  His eyes flicked over in Phir S\textoverline{e}'s direction, his intention clear.



He had a solution in mind.  A way to disable the explosion and stop Phir S\textoverline{e}.



I had only an instant to decide, before the teleporter intervened, or Phir S\textoverline{e} noticed what was going on.



I met Particulate's eyes and nodded once, curt.



The scanner disappeared into a pocket, and he drew something like a grenade from within his flowing coat.  Then he drew the gun on Phir S\textoverline{e}.  I felt the tug of the thread in my hand, attached to the gun.



Without thinking, I hauled on it, pulling it off-target.  The gun hit one screen, two feet to Phir S\textoverline{e}'s right, at stomach level.  It exploded into a swirling cloud of black dust.



Phir S\textoverline{e} whirled around.  He barked out a word I couldn't understand.



``No!'' I called out.



Phir S\textoverline{e} made a gesture with his hand, just as the teleporter flickered into existence.  The man didn't intersect Particulate, but appeared behind him, deftly disarming him of the grenade and pistol before flickering back out of existence.  He took Particulate with him.



``Don't kill him,'' I said.



``You would feel\ldots blameful?'' Phir S\textoverline{e} asked.



\emph{Blameful?  }``Guilty,'' I corrected him, before I realized what I was doing.



I could see the small smile on Phir S\textoverline{e}'s face, disappointed and proud and a condemnation at the same time.  ``I watch you.  In reflection of screen.  You set him up, to put yourself in my good will.''



Had I?  Not wholly consciously.  I'd set up the string, but how much of that was intentional?  Was it habit, now, to have a measure on hand when dealing with any weapon?



I focused on the swarm, focused on the cords and threads that traced the room.  One in the doorway, one at each of Phir S\textoverline{e}'s feet, just waiting for me to finish the deal and bind him.  Others extended between us, spiders poised to cut the threads or tie them, as the situation demanded.



The passenger, or was it me, being wary?



``I guess I did,'' I said.  I made the spiders cut the threads between us.



He shook a finger at me, ``I was not born yesterday.  This silliness could have gotten you killed.  Would have, if I did not feel need for outsider to challenge my ideas.''



``I guess\ldots'' I said, searching for the phrase, ``A gamble's not meaningful if you're not staking something important, right?''



He smiled a little, and there was a slight twinkle in his eye, ``Your life?''



``I suppose,'' I said.  My heart was still pounding, my mouth dry, and it wasn't just the Phir S\textoverline{e} thing, or the teleporter.  \emph{The passenger.}



``You think.  So we know where you stand, now.  You are crafty, dangerous.  Underhanded.  You turn on an ally and use him as a pawn to express something to me.''



``He wasn't quite an ally,'' I said.  ``He helped us get inside this underground base.  But he was reckless.  Breaking into this chamber in the first place, preparing to attack you.  A chaotic element.''



``I do not know this `chaotic' word, but I get your meaning, I think.  There was no communication,'' Phir S\textoverline{e} said.  He smiled as though we shared a private joke.



``I'm doing what I have to, to ensure we all come out of this ahead.  Just like you, but I didn't get the ability to manipulate time, or to create this sort of `time bomb'.  I work on a smaller scale.''



``I get the joke,'' Phir S\textoverline{e} told me.  ``It is joke?  Small?''



``Sort of,'' I said, and I smiled a little in return, behind my mask.  This guy was borderline unhinged, too much power in too unstable a package, and I almost \emph{liked} him.



``What is it you wish to express to me, Weaver, that you would sacrifice a pawn and risk your own life?''



I wasn't sure I had a response to that.  I tried anyways.  ``You want to hit Behemoth with your time bomb?  Okay, let's do it.''



``Oh?  You protested only minutes ago.''



``I'm not about to change your mind, I'm not about to stop you.  So let's make it happen.  We'll let the defending heroes know what's up, set up something-''



``Slower.  Speak slower.''



``Let me go.  We work together with the heroes.''



``The heroes will die in minutes.  Before you arrive.''



I glanced at the screen.  How bad was it?  It was so hard to get a sense of how many heroes still stood.  An ugly feeling gripped my chest.



``We'll try.  Let me try.  I can give you a signal.  You strike then.''



``You are asking me to have faith.''



``\emph{Let me go}, Phir S\textoverline{e},'' I told him.  ``You said you have to stake something that matters on a gamble.  Stake your doubt.''



``I do not understand this,'' he said, suddenly sounding weary.  ``My English-''



``It's not your English; what I'm saying doesn't make a lot of sense,'' I said.  I had to resist the urge to rush and hurry through the explanation.  ``But your doubt, your lack of faith, it's something \emph{safe}.  No disappointments, no fear things won't work out.    Risk that.  Risk losing that.  I did, when I became a hero.''



``Not such a hero,'' he said.  ``Bargain with the madman, turn on an ally.''



``I'm realizing I'm a pretty lousy hero,'' I agreed.  ``But I'm \emph{trying}.  I made a leap of faith.  I'm asking you to as well.''



He smiled a little, then reached forward and took my hand.  He raised it, simultaneously bending over, and kissed the back of it.



``One more,'' he said.



``One more?''



``To wager on a gamble.  A pleasant conversation I might look forward to.  Gone, when you die.''



\emph{Die}?



He spoke a word, and I tensed.  I tried to pull my hand back, but he held on, my fingers wrenching painfully as I tried to get away.



The teleporter appeared just behind me.  His manifestation was followed by a gentle brush of air, as oxygen was displaced from the area his body now occupied.  I could feel my heart skip a beat, the air catching in my throat.



No pain.  A second passed as I made an assessment, realized that he hadn't impaled me with one of his limbs.  Only surprise, and that vague sense of a killer instinct.



The man's hands settled on me.



``Fifteen minutes, Weaver,'' Phir S\textoverline{e} told me, releasing my hand.  ``Fifteen minutes, or if the heroes cannot put up fight any longer, whichever is first.''



And I was gone, out of the basement, planted in the midst of the battlefield.  Phir S\textoverline{e} wasn't even in my range.  I'd made the call to work with him, and now it was set in stone. There would be no going back to change his mind, to stop him.  He'd strike, guaranteed.



Even with the filter of my mask, the smell of ozone and the heated air burned the edges of my nostrils.  Acrid smoke was so thick in the air that I could taste it, breathing in through my nose.



And Behemoth loomed in front of me, \emph{far} too close for comfort, his silhouette shrouded in the smoke around him.



I turned and activated the antigrav panels, running to help get up to speed before it could help me lift off.  



The ground abruptly tilted under my feet, a steep shelf of street and underlying rock rising in front of me, blocking my path.  I managed to grab the uppermost edge with my hands, hauling myself forward enough that the flight pack could take over.



No bugs.  I'd left them behind in Phir S\textoverline{e}'s lair.  If I'd thought about it, I might have asked for time to collect them.  At the same time, I couldn't have spared the minutes.



Two or three thousand bugs, the only silk I had were the cords that were still attached to me, the ones I'd stretched between Phir S\textoverline{e} and myself and then cut.  I had my taser, laughably petty in the face of Behemoth, a small canister of pepper spray, and the flight pack.



Long odds, even at the best of it.  I pressed the button on my armband, spoke into it, and got only silence in response.



My bugs moved throughout the battlefield, and I marked every cape I came across.  Shelter was scarce, and hard to make out in the smoke.  Each flash of lightning marked an unfortunate cape who'd found themselves too far from cover and in Behemoth's sights.



In the midst of it all, I could speak and I couldn't make myself out.  It was almost like being in Grue's darkness, before his second trigger event.  Couldn't see.  Couldn't hear.  My movements, even, were harder to judge.  I felt like there was a pressure, here, as if the smoke had substance, and even Behemoth's existence, somewhere nearby, was weighing on me.  Was I tired, or was everything heavier?  Or, it struck me, maybe the oxygen content in the air was lower.



I wasn't sure about the ramifications of that.



So few bugs to draw on.  Five to ten touched a single cape, allowed me to check if they were anyone I recognized, then all but one would leave.  One bug per cape, the rest scouting.



Ligeia was the first I recognized.  The conch shell mask, one of Accord's people.  Citrine would be close by\ldots



Or not.  I swore under my breath, touched ground to reorient myself, then hurried around a corner.



She was creating a massive portal, widening it with every passing moment.  It made me wonder if there was a reason there were so few recordings of the Endbringer attacks, if the PRT hid this sort of thing.  They'd hidden the particulars of the Echidna attack, and one of the reasons Alexandria had argued, a reason \emph{I} had argued in favor of that, was because it wouldn't go over well with the public to know just how much devastation a single parahuman could be capable of.



Her portal was perhaps twenty feet across, circular, and cold water gushed out, as if forced by an incredible pressure.



It was the sort of defensive measure that you employed when there weren't any frontline combatants left.  A desperate, violent one, like Sundancer's sun.  My bugs found her ear, and I communicated as clearly as I could, ``\emph{Run}.''



She didn't hear.  Doggedly, she stood her ground, drenching Behemoth, widening the portal's radius.  So hard to tell just how much, without losing bugs to the spray.  Twenty five feet?  Thirty?



``\emph{Run},'' I tried again.  I muttered, ``\emph{Run}, Ligeia.''



He erupted with lightning, and I could momentarily see his silhouette in the distance, the light cutting through the thick clouds of smoke and dust.  I could see the tendrils of lightning as though through a strobe light, holding positions as they followed the flow of the water, then changing to other targets, finding solid conductors to latch onto.  The entire geyser was lit up.



She changed tacks, and the portal began \emph{sucking}.  The lightning disappeared, and Behemoth stumbled forwards towards the opening, the water now reversing direction.



Eidolon appeared like a spear from the heavens, striking him between the shoulderblades.  Behemoth nearly crashed through.  His claw settled on the portal's edge, as though it had a physical mass to it, slipped through.  The lightning wasn't traveling far, now, and the image of it was soon lost in the smoke.



The portal closed, and Behemoth managed to claw his way back, simultaneously fending off Eidolon, the lighting growing stronger with every passing second.



He lurched, and dropped several feet, the ground shaking.  The light show marked the geyser spraying up around his leg, apparently having sunken into a portal.



\emph{Close it}, I thought.  \emph{Sever it.}



But she didn't.  Not an option, it seemed.



\emph{Move, Taylor}.  \emph{Deal with your own jobs first.}  How long did I have?  Fifteen minutes?  Thirteen?  Twelve?  So hard to keep track of time right now.



My underlings.  Wanton, he was nearby.  \emph{Larger}.  He carried stretchers with the wounded, which moved around the very periphery of his range, where they rotated slower, and other objects closer to his core.  An armband, a dismembered arm with scorch marks at the base.



His or someone else's?



Once I caught up to him, I found the others a distance away.  Tecton had fashioned something crude to attach to his armor, a shelf on his back that would hold injured capes.  He rode his three-wheeled bike forward, stopped to slam his piledrivers into the ground to erect a wall of stone, punched through an obstruction, made more forward progress, and then created another wall.  A staggered retreat.  Grace, Cuff and Golem followed, each with wounded behind them on their vehicles.



Annex?  I couldn't find him with my bugs.  He was either swimming alongside them, helping to clear the way, or he was injured.



I was on my way to catch up to them when Ligeia was struck down.  A chance lightning bolt had struck her, just like that.  Behemoth surged to his feet.  Lightning traced the arc of the water that still geysered up, less impressive with every passing second.



Even killing her hadn't forced the portal closed.  \emph{Damn}.



I came to a stop at Tecton's side.



``Sorry,'' I panted.  My voice sounded so rough-edged.  \emph{So hard to breathe}.



``Tecton can't talk,'' Cuff said.  \emph{Her} voice was oddly level, in contrast to how she'd acted early in the fight.



``What happened?''



``Clipped by another cape,'' she said.  Still with no emotion, no affect.



``Doesn't matter,'' Grace cut in.  ``Where the fuck were you?''



Tecton's hand moved, settling on her shoulder.  Grace backhanded it away.



``I found what Behemoth wants,'' I told her.  ``Where's Rime?''



``Dead,'' Golem said.  He carried a small child, and was falling behind,



``Who's next in command?''



``Prism, but she's injured,'' Grace said.



``I need to communicate with someone in charge, and we don't have time,'' I said.  ``Dragon?  Defiant?''



``Metal suits are all toast,'' Grace said.  ``No clue about Defiant.''



``Revel?  Your boss?''  I asked.  Then I corrected myself.  ``\emph{Our }boss?''



``Saw her two minutes ago.  No word on chain of command.  She said we should run, take anyone we can help.  Scion's dropped off the radar, but last we heard, he was heading \emph{north}.  Not east, not west.  He has to be \emph{trying} to avoid this fight,'' Grace almost snarled the words.



``It's not hopeless,'' I said.  ``We've got a shot, here.  Behemoth's target is a weapon.  Kind of.''



``A weapon?'' Golem asked.



``A bomb.  Maybe big enough that it makes an atom bomb look like a hand grenade.  Something that's supposed to take down Endbringers.''



``No shit?''  Grace asked.  I could see a trace of hope in her expression.



``An \emph{energy} weapon,'' I clarified.



I saw that hope become confusion.  ``But that's-''



``It's something that could go \emph{really} right or \emph{really} wrong,'' I said.  I saw the confusion become a momentary despair.  ``Which is \emph{exactly} why we need to get in touch with someone that matters.  \emph{Where} are the heroes?  Where was Revel?''



Golem pointed.  ``That way.''



``Citrine?  Woman in yellow dress.''



``Yellow bodysuit now,'' Golem said.  ``She stripped out of the dress when he pushed past the command center.''



Fuck me.  Now that he mentioned that, I couldn't help but wonder if I'd sensed her with my bugs and dismissed her as a stranger.



``I think I know where she went,'' I said.  \emph{Same direction Revel went}.  I was already lifting off the ground.  ``Go, drop off injured, then come back if you can.''



``Revel told us to scram,'' Grace said.



``I'm telling you that we need to distract that motherfucker for \emph{five} seconds,'' I said.  ``Where's Annex?''



``Here,'' Annex said, from behind me.



I turned to look as he stepped out of a building.



``You're with me,'' I told him.  He didn't have any wounded with him.



``I need to ride something,'' he said, ``Not fast enough.''



``Define `something','' I told him.



``Something heavy enough to hold my entire body mass.''



Could I hold an entire other person?  No.  I could hold a child, but that'd be a stretch.



``Climb inside my costume,'' I told him.  ``The flight pack too.''



He gave me a bewildered look.  ``You realize I'd be right against-''



``Move!''  I barked.  How long did I have?  Not enough time.  Modesty was \emph{not} an issue.



He flowed into my costume, and I could feel him against my skin, his body strangely cold and smooth.  A lump of him stuck out over one shoulder.  His head, not quite normal, not quite his specter form, had formed itself in my shoulderpad.



And we were too heavy for the antigravity.



I'd have to gamble, make compromises, take risks.  I looked to the others, ``Reach deep inside, find your second wind.  Find your \emph{third} wind, if you can.  Rendezvous with me over there if you can make it in eight or ten minutes.''



Then I deployed my wings, activated the propulsion system alongside the antigrav.  It was slow to lift off, but it was faster than running. 



If I got shocked, or if the electromagnetic radiation got any worse, this could cut out on me any second, but I needed to \emph{move}.  I needed assets, even if I didn't know for sure what I'd do with them.



The Chicago Wards peeled away behind me, abandoning the defensive walls and careful retreat in favor of speed.



We found the defensive lines in a minute, if that.



The Undersiders were there, fighting.  Three stuffed goats and the dogs provided an added barricade for them to hide behind, while Foil was firing her needles.  Regent held her quiver, handing her bolts to fire, while Imp lurked on the far side of the street, her back to the wall.  Citrine was peering between two dogs, erecting a field of golden light near the Endbringer.



Grue wasn't with them.



``Gah!''  Regent cried out, as I landed, folding the wings back into place.  ``Jesus fuck!''



Right, I had two heads.  ``Out, Annex.''



Annex flowed out of my costume and straight into the ground.  Within seconds, he was shoring up the wall, drawing in debris and using it to rebuild and reinforce.



``Where's Grue?'' I asked.



``Hospital.  Burns,'' Imp said.



I nodded.  ``Bad?''



``More mentally than physically.''



\emph{Ah.}



I could only hope he'd bounce back.  To business. ``Revel.  American cape with sort of an Asian-themed costume, lantern.  Where is she?''



``Zapped,'' Regent said.



\emph{You've got to be fucking kidding me.}



My disbelief was tempered by a measure of alarm.  I was limited in time, and that was bad enough, but if Phir S\textoverline{e} decided our defending forces weren't sufficient to put up a fight, he could strike sooner.  If \emph{I} couldn't find someone capable of leading the defense, if we were little more than scattered remnants, why would Phir S\textoverline{e} wait?



``Revel absorbs energy, kind of,'' I said.  ``She might be okay.''



``She got hit by \emph{lightning},'' Regent told me.  ``Kind of lethal.''



Rachel snorted.



I glanced at the dogs.  She didn't seem to mind that they were somewhat exposed, huddled against the ruined wall the Undersiders were using for cover.  One of the dogs seemed to be reacting badly to the lightning strikes, and was huffing out deep, very un-doglike noises each time one struck nearby.



``Listen,'' I said.  I flinched as lightning touched nearby.  He was focusing more on a \emph{quantity} of bolts than on the really heavy hits.  Cleaning up the remanants of our defenses.  ``Revel.  Where did she fall?  Or you could point me to anyone else that might be in charge?''



Parian pointed, almost absently.  I couldn't tell if she was dismissing me or if her focus was taken up by the stuffed goats.  One took a lightning bolt, and she was patching it up and reinflating it within a second.



I took off.  Again, I tried my armband.  Static.  Better than nothing, but not ideal.



I passed over the contingent of Y\`{a}ngb\v{a}n.  Just getting near them, I could feel my powers swelling, my range growing, a crackling at the periphery of my attention.



And then it was gone.  I was leaving them behind.



Eerie.  Uncomfortable, even, with the recent reminder of how my powers were feeling vaguely out of my control.  A boost in range wasn't worth any surprises on that front.  Bugs were almost useless here, \emph{more} bugs wouldn't make a difference.



Revel was in Dispatch's company, alongside a cape in white, with a starburst worked into his helmet, radiating from the eyeholes and the gap for his mouth.  She was lying down, using a piece of rubble for cover.  She stirred as the ground rumbled, marking Behemoth's rapid footsteps.  Not a \emph{run}.  It felt off, saying something like him was running.  But a \emph{lope}, like how a gorilla might move, that fit.



``She conscious?''  I asked, as I landed.



``She \emph{is},'' Revel answered for herself.  She seemed to have to work to focus on me.  ``Weaver?''



``I found what Behemoth is after.  Who can I talk to?''



Dispatch stepped out of the way, so the man in white with the starburst helm was free to act.



``Me,'' the man in white said.  ``I'm Exalt.  Interim leader.''



``The Texas Protectorate leader.''



``Houston Protectorate, yes.''



``A local cape has gathered up a whole mess of energy.  Enough to wipe India off the map.  He's planning to hit Behemoth with it, in two or three minutes.''



``It won't work,'' Exalt said.



``I \emph{know} it won't work.  But he's going to try, no matter what we do, and we need to distract the Endbringer long enough to give it a \emph{chance}.''



He exchanged glances with the others.



\emph{Hurry}, I thought.  I was panting, my mouth thick with the taste of ozone.  Even with my lenses, my eyes were watering from the peripheral smoke.



``Go,'' Revel said.  ``Expend it.''



\emph{Expend}?



``It's too soon,'' Exalt said, ``And we don't have all the informat-''



``No time!  Decide now!''



I saw him hesitate.



Swearing under my breath, I turned on my heel and flew away.



I was burning bridges, but that was a hell of a lot better than everyone here dying.  How long did I have?  I couldn't even begin to guess.  Two minutes?  Eight?



Big difference between the two.



Fuck it.  A waste of time.  I'd burned precious minutes finding them, and they'd been too slow to help.  I wasn't sure I could work with the Protectorate, with the Wards.  Not if they failed us like this at this crucial juncture.



Assets.  Didn't have enough resources here.  We needed to pull something decent, something that could\ldots



I had no fucking idea.  How were we supposed to keep Behemoth sufficiently still and distracted, controlling a detonation that had the potential to level a continent?



The Chicago Wards were arriving, minus Wanton.  I signaled them with bugs to fine-tune the direction they were traveling, putting them en-route to the Undersiders.



And behind me, as if they were feeling guilty, Exalt and Dispatch were giving chase, rapidly catching up.  Dispatch moved in bursts of speed intersped with moments where he ran at a normal pace, Exalt flew with Revel in his arms.



I found the Y\`{a}ngb\v{a}n and approached.  They were reacting even before I'd landed, turning, hands raised to attack.  There were twenty of them, or close to.



``English?'' I asked the Y\`{a}ngb\v{a}n.



They were silent, almost \emph{cold} in response.



They were nationalist capes.  I was a foreigner, maybe an enemy by default.



``English, please.  This is it, the deciding moment.  Your help, it's\ldots it's essential.''



No response.



Exalt, Revel and Dispatch were slowing as they approached me.  I drew an arrow in the air with the few bugs I had left and pointed them to the Undersiders.  They ignored the instruction, setting down just behind me.



``Weaver,'' Exalt said.  His voice was grim.  ``They aren't allies.



``We need all the help we can get,'' I said.



``The Y\`{a}ngb\v{a}n pulled an assassination attempt on Chevalier,'' Exalt told me.



My eyes widened.



``A traitor among us,'' a young man spoke, his voice badly accented.  Another snapped something at him, and he responded in Chinese.



None of the heroes replied.  I couldn't bring myself to speak, couldn't think of a single thing to say that would be remotely diplomatic, in the midst of this.



``We \emph{do} need all the help we can get,'' Exalt said, not taking his eyes off the group.  ``You want to make amends?''



The English-speaking one translated for the others.  I fidgeted nervously.  How many minutes, now?  Why hadn't I asked for more time?



``\emph{Sh\`{i} de}!'' one cried out.



``Sh\`{i} de!'' the group called out in unison.



``That's a yes,'' Exalt said.  He was already turning, taking flight.



Twenty Y\`{a}ngb\v{a}n members.  Exalt.  A dazed Revel.  Dispatch.  The Chicago Wards.  The Undersiders.  Citrine.  Me.



The sum total of our defensive line.



And Behemoth was getting too close.  A hundred and fifty feet?  A hundred and twenty? He was swiftly approaching the hundred-foot mark we'd been warned about, where he could close the distance with a single leap.



There were so few heroes capable of holding him back.  He was covering ground at twice or thrice the speed he had been earlier, and the Undersiders didn't have the means to \emph{know}.  They were on the ground, blinded by the ambient smoke and the dust of the hundreds of buildings that had fallen across the city.



``\emph{Run},'' my bugs communicated.  But nobody responded, nobody reacted.  Too much ambient noise.



\emph{Run}, they spelled out words, shaping letters with their bodies.  Too much smoke.



I bit them, stung them, and that spurred them into motion.  Maybe too late.



He wasn't even a full city block away from them.  Only a few half-destroyed buildings stood between him and the Undersiders.  They were still sorting themselves out, getting mounted on the dogs for a retreat, but it was too little.



Behemoth leaped.  Not the monumental leap he'd used early in the fight, but a leap nonetheless.  He landed in the midst of a building, knocking much of it over, and the impact was enough to bounce Citrine off one dog, to knock Tecton over.



The Endbringer had closed half the distance.  A mere twenty feet separated them from his kill aura, if that.



I landed beside Citrine, helping her up, using my legs and the antigrav to try and help her  onto the dog's back.  She kicked her heels the second she was seated, shouted an order I couldn't make out.



The dog, scared, growled and held its ground against Behemoth.



``Rachel!'' I screamed the word.  ``Call him!''



She whistled, sharp, and it seemed to break the spell.  The dog lurched around and ran, nearly knocking me to the ground.



The Y\`{a}ngb\v{a}n were landing in the Undersiders' midst, joining the fray.  I could feel my power swell, my range increasing by one block, two\ldots



I could sense the underground complex, where Phir S\textoverline{e} was.  He swatted absently at the bugs that had been left behind, uncontrolled in my absence.



``\emph{Wait},'' I communicated to him.  ``\emph{Almost}.''



Either we'd manage this in the next few minutes, or we'd be dead and it wouldn't matter.



I called the bugs, leaving only enough to speak to Phir S\textoverline{e}.



The Y\`{a}ngb\v{a}n opened fire with lasers, and erected forcefields to ward against the lightning bolts.  Golem's hands rose, faster with the Y\`{a}ngb\v{a}n's help, but too slow to make a substantial difference.  Tecton's walls, similarly, couldn't rise high enough to block Behemoth's line of sight.  The power boost would increase his tinker abilities, but it wouldn't empower the \emph{results} of his technology.



Citrine's power intensified in the depth of the yellow-gold light, in size.  Grace shimmered, Cuff was better armored, Annex covering more ground.



Why couldn't the Y\`{a}ngb\v{a}n have helped like this sooner?  From the very start of the fight?  Damn people.  Damn them all, for their idiocy and selfishness and their small-mindedness.



This wasn't enough.



Behemoth reached out, and lightning plowed through our ranks, left to right.  The Y\`{a}ngb\v{a}n forcefields fell in the lightning's wake, and Tecton was struck from his bike.  Cuff was too far back, unprotected, dropped in an instant.  I ducked low, covering my head, as it crashed against a quadruple-layer of forcefields the Y\`{a}ngb\v{a}n had provided.  One of them was knocked prone as the last forcefield shattered.



A stray Y\`{a}ngb\v{a}n member, too far to the right, was knocked to the ground.  She started to struggle to her feet, then collapsed a second later.



Revel flew to the injured Wards, but didn't have the strength to stand.  Instead, she raised her lantern, ready for the next strike.



The Y\`{a}ngb\v{a}n hadn't even raised their forcefields again when he hit us with lightning once more.



Revel absorbed the initial impact, sucking it into her lantern.



I wasn't close enough to benefit.  I saw the lightning twist in the air as Behemoth swept his hand out to one side, striking another two Y\`{a}ngb\v{a}n members, just out of the lantern's reach.



Dispatch appeared next to me and other Y\`{a}ngb\v{a}n members, and in an instant, everything went still, quiet.  My ears roared with a high pitched whine.  My breath sounded too noisy, my heart beat so fast I couldn't even see straight.



Like Clockblocker's power extended a temporal protection, almost impossible to break, Dispatch's power seemed to do the same, even if he was effectively achieving the opposite, accelerating us with the outside world moving at a snail's pace.



The effect ended just as Behemoth moved on to other targets.  Another Y\`{a}ngb\v{a}n member was struck down.



And, inexplicably, he continued his lightning strike, carrying over to the far end of the street.



There was a yelp, and I could see Imp, all at once, sheltered by a wall that was shrinking in size with every second the blast continued.  She held the Y\`{a}ngb\v{a}n member who'd strayed too far away from our main group in her arms.



He'd seen her.  Sensed her.  And now, behind a wall no more than three feet high, she had nowhere to run.



I pushed past Y\`{a}ngb\v{a}n members, unstrapping my flight pack, \emph{tearing} at the parts that fed down to my gloves, to get it off.  If I could get it to her\ldots



I couldn't.  I stopped, the pack in my hands.  The lightning would break the thing before it could carry her away.



\emph{If Grue's alive, he won't be able to forgive us for }\emph{letting her die}.



Citrine drew a yellow glow around Imp, and the lightning fizzled as it passed the perimeter.



The Endbringer switched to fire, and it passed through.  It seemed to halve in intensity, but that was enough.  I could hear Imp scream in alarm and fear.



He advanced a step, and the fresh angle afforded her even less cover.  His kill aura\ldots if he simply ran forward a few steps, he'd murder us all in seconds.



But Golem's hands held his legs.  One had sunk deep into a pit, hands of pavement gripping the knee, melting at the close contact, even as others rose to reinforce.  The other leg was raised, but held in much the same fashion.



Imp screamed again as he directed another wave of flame her way.  It was a scream of pain this time.



Foil shot him, but he didn't turn away from Imp and the Y\`{a}ngb\v{a}n member.  Instead, one hand stretched out, casting flame towards her.  The cloth goats blocked it, and were promptly set aflame.  He maintained two columns of flame from his hands, one directed at Imp, one at Foil and Parian.



Revel launched a mess of spheres at his chest, and the surviving Y\`{a}ngb\v{a}n followed up with lasers.  Behemoth simply maintained the assault, almost uncaring as the lasers and disintegration spheres ate into his torso.  Negligible damage, in the grand scheme of things.



``Fuck it,'' Regent said, his voice almost inaudible.  He was looking at Imp.



``Regent,'' I said.  When he rose to his feet, I raised my voice, ``Regent!''



``Hey Shitcrumb!''  Regent hollered, backing away from cover.  ``Easy-''



Behemoth dropped the flame attack.  I could see Y\`{a}ngb\v{a}n members raising forcefields as he reached out, casting a bolt of lightning in Regent's direction.  The forcefields did nothing, not even softening the blow in any measurable way.



Regent was snuffed out, dead.



A small sound escaped my mouth.



But there was no time to react.  Reeling, grieving, it would cost us.  He'd done what he did for a reason.  The antigrav on the flight pack kicked in, I waited until it started to drag me, then let it go.  It skidded across the gap, across the road, to Imp.  She caught it, and I controlled the motion of it to drag her away.



``\emph{Retreat}!'' I called out, and my voice was strangely ragged.  ``Citrine, cover!  We need forcefields too!''



And Exalt.  We needed whatever power he could bring to the fore.



Eidolon landed between us and Behemoth.



He said something I couldn't make out, then raised his hands.



A forcefield, taller than Behemoth, separated us.  For seconds, Behemoth was muted.  He swiped his claws at the forcefield, fell short.  He couldn't advance, with the way Tecton and Golem had him held with one leg buried up to the knee, couldn't reach far enough to touch the forcefield.



One claw dashed a hand of asphalt to pieces.  Golem started to raise another to replace it, but Behemoth torched it, turning it to a liquid or a glass.  Something flat, shiny.



We pulled ourselves together.  I changed Imp's direction, brought her to us.  She let go, and the thing careened dangerously, striking the ground a little too hard.



She crouched by Regent, touched his throat.



She shouted something.  A string of swear words, insults aimed at Regent.



``\emph{Come on}!'' I screamed the words at her.  It took me a second to get the flight pack going again.  I steered it, like a fish on dry land, towards her, as Rachel hauled me up onto a dog's back.



``Weaver,'' Phir S\textoverline{e} said, almost half a mile away, still in the room with the monitors, ``If he advances any closer to me, I won't have any option but to strike.



``\emph{Wait},'' my bugs communicated.



Reluctantly, Imp reached for the flight pack, hugged it to her chest.  Not the best option, given the options I had for controlling it.  Still, it was a way to get her moving towards us.



Some heroes were pelting Behemoth from another direction.  So little, in terms of effect, but it was a distraction.



We needed to regroup.  Needed to form some kind of plan, however haphazard.



Fuck it.  Foil had the facemask\ldots who else?  Citrine and Foil\ldots the back of the head of the dog they rode.  Dispatch wore a helmet\ldots but I could use bugs to draw an arrow on the ground.  That left Annex, where the hell was he?  My bugs couldn't sense him.



My eyes could.  In the midst of the smoke, I saw the bike Tecton rode was lighter than the rest.  Annex was inside it.



I pointed them in the same direction I'd sent the others.



We converged on the same point.



``Dispatch!'' I called out.  ``Huddle!''



He reached the midst of our group, and his power surrounded us.



Silence, stillness.  The buzz of my power at the periphery of my consciousness was a fraction of what it might otherwise be, limited to the bugs that crawled in the recesses of my costume.  There was only the press of bodies, two dogs and all of the rest of us in an area smaller than my jail cell.



I tried to speak, and emotion caught my voice.  It threw me, as if it didn't match how I felt, didn't match the composure I felt like I had.



Nobody cut in, nobody used the silence to venture an opinion.



When I did speak, I did it with care, shaping each word, speaking slowly, so I wouldn't embarrass myself again.  ``How long?''



``This?'' Dispatch asked.  His voice was low, grim.  ``This many people?  Those dogs?  Four minutes.  Maybe two, if we're all breathing this hard.  Once we run out of air, I gotta cut it out.''



I nodded.



\emph{Think, think}.



``Sorry about your pal,'' Tecton said.



I shook my head.  A denial?  He \emph{was} important to me, but\ldots what, then?  Was I wanting to focus on the situation?



``Not now,'' I said, sounding angrier than I meant to.  ``Need a plan.''



``A \emph{plan}?'' Dispatch asked.  ``We run.  We pray.''



``Last I heard, Scion was nowhere near,'' Foil said.  ``Nobody to pray to.''



``Not funny,'' Dispatch said.  ``This isn't the time to fuck around on the subject of God.''



I shook my head again.  Plans.  Options.  I had an idea, half-formed in my head, and I couldn't bring it to the fore.  Some missing element.



``Rachel.  You wanted revenge on that motherfucker?''



``Yeah,'' she said, ``Leviathan killed my dogs.''



``Behemoth killed your friend,'' Tecton added.



``And Leviathan killed my dogs,'' Rachel said.  ``They both pay.''



``They both pay,'' I agreed.  ``What the hell's Exalt's power?''



``Aerokinesis and telekinesis,'' Dispatch answered me.  ``But he spends a charge, takes a day or \emph{days} to build it up again.''



Which explained why he hadn't helped.  Fuck.



``Eidolon's power\ldots he chooses what powers he gets?''



``He gets the powers he needs,'' Dispatch said.  ``He can be receptive to new ones, hold tighter to ones he wants to keep, but that's it.''



I nodded.  He was at the mercy of his passenger, it seemed.



I glanced to my right.  ``Foil.  Can you use your power on just the \emph{tip} of an arrow?''



``Yeah.  But why would you want me to?  Fucks up the trajectory.''



``Just thinking,'' I said.



``You have a plan,'' Rachel said.  There was a measure of smugness in her voice.  No, I was reading her wrong.  Satisfaction?



``Maybe, yeah,'' I said.  I glanced at the space outside the bubble.  The people were moving at a glacial pace, heads turned our way.  Eidolon flew in the sky above.  ``We need to hurt Behemoth, and hurt him badly enough that he gets distracted.  Then I signal Phir S\textoverline{e}, and hopefully we aren't vaporized in the wake of all that.''



``Explain,'' Dispatch said.



``Each of us has a role to play,'' I said.  ``Timing's essential.  So's luck\ldots''



\sectionbreak



The bubble burst, and we moved into action.  Behemoth had barely advanced from his position.  The others were still running.  We'd earned ourselves two minutes to think, to plan and discuss.



I'd gathered countless bugs through my journey across the city.  I'd briefly lost track of them when I was teleported away from Phir S\textoverline{e}, but they were still \emph{there}.  Relatively few had died, even from the start, their lives thrown away to test the boundaries of fires or gushing water, or shielding people from the roar.



A lot of bugs, held in reserve.



``Golem!''  I called out.  ``Metal hands.  Doesn't matter how big.  Find a way.''



He glanced at me, still jogging away from the Endbringer.  Still, he managed to find a shop with a metal shutter at the doorway.  He plunged his hand inside it, and hands appeared in various places across the street.  A large one from a rickshaw, another from a car's engine block, small ones from the metal grilles covering windows.



Half of my bugs gathered.  Another half began chewing through power lines.  The transformers here were nightmares, tangled messes, and had an abundance of wires.



Each of the others was carrying out their tasks, their roles.  Rachel had a chain stretched between two dogs, and was attaching the chain from one dog's harness to it to extend the thing further.  Annex stretched it further, extending it so each link was nearly two feet long, thin.  Citrine was tinting the area between us and Behemoth.



Dispatch called to Eidolon, and the ex-Triumvirate member descended.  Dispatch contained them.



Eidolon needed time, and he needed to hear the details of our plan.  Dispatch would give him both.



In the distance, Behemoth pushed his way through the forcefield, shattering it.  We had a minute, if that.



I waited impatiently as the others tended to the chain.



Dispatch's effect ended.  He and Eidolon relocated to the other end of the street, Dispatch took a second to catch his breath, and then he used his power on Eidolon again.



\emph{Come on, come on}, I thought.  This could go awry with one lucky shot from Behemoth.



``Yangban!'' I shouted, no doubt mispronouncing the title.  ``Forcefields!  Protect the teams!''



Lightning crashed against the forcefields only moments after they went up.  Some diverted to the metal hands.



And my swarm started to arrive.  Millions of insects, bearing power lines that they were still stripping of insulation, hauling the wire itself, bearing the ones who bore the wire in turn, or hauling on silk that was attached to the wire.



I'd hoped to drape it over the hands, to wrap it around.  I was forced to attach it to the base of the hands instead.  Too heavy to move otherwise.  Conductive hands, conductive wire.



``Go!'' Foil shouted.



The dogs moved.  Bitch rode one, hollered commands to get them to stay apart.  The chain stretched taut between them, long, thin.



I saw Dispatch's effect end.  Eidolon took flight, following.



``This'll work?'' Imp asked.  Her voice sounded more hollow than Grue's did when he used his power.  I jumped a little to hear her suddenly speaking beside me.



``I don't know,'' I said.



``Because if this is revenge for Regent, it has to work.''



``It's for him if it works,'' I said.



``Mm,'' Imp said.  ``I'll kill you if it doesn't, then.''



``We're all screwed if it doesn't,'' I said.



``Mm,'' she said, and she didn't say anything else.



The Endbringer lashed out with a mess of lightning.  It caught one dog before it disappeared behind cover.  The dog slowed, but it recovered and found its pace, redoubled its efforts to catch up, as Rachel continued to shout commands to keep the chain taut.



Behemoth used fire, instead, targeting Rachel, and Citrine's power dampened the effects.  That was her role in this.



It was just a question of whether it would run out prematurely, if the dogs would get far enough.



He clapped, and a shockwave tore through the area.  Rachel was already directing the dogs; they moved so there was cover, buildings between them and Behemoth.  The chain, imbued by Foil's ability to shear through anything, cut through the buildings as though there was nothing there.



And just like that, they made it.  The dogs passed Behemoth, a hundred and twenty feet of chain maintained between them, and the chain cut through him as easily as Foil's arbalest bolts had.



Too low.  There was just a little slack, and they weren't high enough off the ground.  The chain cut through the soles of his feet, through the lower part of one ankle.  Insignificant.  He didn't even fall over.



Then I heard Rachel through my swarm.  A shout.  ``Back!''



The dogs stopped, one doing so so abruptly that Rachel was nearly thrown to the ground.  Nearly touched the chain, losing a limb.



The Endbringer moved his hands in anticipation of a clap, and Exalt used his power.  Blades of wind, a hundred strikes in a moment, a thrust of telekinetically controlled air from across the city, rushing past Behemoth, making the Endbringer stumble.  The clap arrested.



Rachel held on as the wind hit her, held on as each dog turned a hundred and eighty degrees.  They passed Behemoth a second time, only this time, Rachel shouted another command.  One of the first I'd heard her give.  I knew now that it was the command for `up'.



Her dog leaped up to the highest point on a ruined building, and the chain caught Behemoth at the knee this time.



They got halfway before Foil's power wore off.  The dog tumbled in midair, Rachel thrown, flipping head over heels.



Behemoth crashed to the ground, one leg a stump.



Eidolon caught Rachel with one arm, and extended the other towards Behemoth.



``\emph{Now},'' my bugs told Phir S\textoverline{e}, as the field surrounded the Endbringer, a forcefield, extending into the Earth, surrounding Behemoth on all sides, a cylinder.



Phir S\textoverline{e}'s portal opened beneath Behemoth's feet, aimed upward, and a plume of light speared into the sky, consuming Behemoth, covering him.



Eidolon's power held.  He'd had the situation explained, had been given time to let his power build up to full strength, and his passenger had supplied something with a durability on par with Clockblocker's ability.  Inviolable.



``That'll do,'' Imp said, quiet.  The light continued to flow upward, a narrow column no more than fifty feet across, billowing out only slightly as it reached the top of Eidolon's barrier, parting smoke and clouds in a circular ring, revealing the intensely blue sky above.  The entire sky seemed to brighten as the light dissipated beyond our atmosphere.



Phir S\textoverline{e}'s light faded, and the barrier collapsed.



Dust continued to fill the area, plumes of it.



Behemoth lurched forward.



Not quite \emph{Behemoth}, but a skeleton, something like a skeleton.  Emaciated, a black-red frame dripping with ichor, it had all of the key features, the basic underlying structure with the horns and the gaping mouth, the claws and the way the shoulders were broad enough to host his bulky frame, but a good eighty percent of him had been torn away, shredded.  A skeleton covered in a veneer of meat.



``\emph{Go},'' I whispered, feeling a quiet despair.  ``Go home.  Go underground.  Leave.  We hurt you as badly as we've ever hurt you bastards.  That's enough.''



He reached out, and lightning reached across the landscape, striking Golem's metal hands, into the grounding wires I'd rigged.  The hands melted with the intensity of the strikes.



Behemoth wasn't any weaker than he had been.  Not in terms of what he could dish out. As much as he was wounded, he was \emph{healing}.  Even from where we stood, I could see him healing, flesh expanding, swelling, regenerating.



The Endbringer lurched forward on three intact limbs, starting to glow with that radioactive light of his.  He was ignoring or ignorant to Eidolon's escape, as the `hero' carried Rachel away, the dogs following on the ground.



He was continuing to make his way towards Phir S\textoverline{e}, who had formed another portal, was gathering power for a second strike.



``Retreat,'' I said, only to realize I wasn't loud enough for anyone but Imp to hear.  I raised my voice for the others.  ``Go!  Retreat and regroup!''





