





The damage Behemoth was wreaking in New Delhi was, I thought, a microcosm of what was happening all over the world.  Three or four attacks a year, since the Simurgh had appeared.



The fight with Leviathan in Brockton Bay had been a good day.  We'd lost people, we'd lost good capes, but we'd more or less bounced back, made it three-quarters of the way back to where we needed to be, in a matter of months.  There had been ugliness, infighting, a hell of a lot of doubt, but we'd started to make our way back to where we should be.  It had been the lowest number of casualties we'd had in an Endbringer attack in years, not counting a few of the Simurgh attacks.  A good day.



\emph{This?  This isn't a good day. }



Behemoth roared.



\emph{This is the other end of the scale.}



For nearly twenty years, we'd endured intermittent Endbringer attacks, and the end result was, globally, what was happening here in a matter of hours.  We were divided, scared, fighting among one another, and our defenses were being eroded.  We were being forced into pockets of defense, instead of a united one where we all stood together.  Those pockets, in turn, were at risk of being wiped out with a series of decisive blows.



Yes, we had our good moments.  Doing as much damage to him as we just had, that was a good moment.  But we had bad ones too, and the end result was always the same.



The bastard –\emph{the bastards, plural}– kept coming.



Phir S\textoverline{e}'s light had cleared smoke and dust from the sky, though it had been almost entirely directed upward, with concentric rings still marking the skyline.  Smoke was free to rise, and Behemoth was in plain sight.  He was moving on three limbs, planting hands on the ruined, half-toppled and flame-scorched buildings to stay more upright.



His body, though, was a mix of high contrasts.  His flesh, what little was visible through the black ichor that dripped from his frame, glowed a silver-white.  The remaining material of his claws, teeth and horns remained black.



Tecton had pulled ahead of the group, and turned abruptly, skidding to a stop.  Cuff's body was folded over the back of the bike, limp.  The Y\`{a}ngb\v{a}n had two more bodies with them, as well.  I'd taken my flight pack back from Imp, and was airborne as he raised a gauntlet to get my attention.  I descended to meet him, and we were soon joined by Dispatch, and Exalt, who carried an unconscious Revel.



``Where to?'' Tecton asked.  His voice was hoarse.  He was recovering, it seemed.



``If we're sticking with the regular plan,'' Dispatch said, ``We should gather with other capes, form another defensive line.  I think we should hold to the plan.  Working together with a less than ideal plan is best, until we can come up with something better.''



I glanced over my shoulder at Behemoth's barely visible profile.  How far away was safe, if he was emitting that kind of radiation?



\emph{Far, far away}, I answered my own unspoken question.



``Weaver?'' Tecton asked me.



I ventured, ``There's a temple, not far from here.  Tattletale's there, medical facilities.  Direction he's moving, he's headed in that general direction.  We protect them, hold position, see if we can't figure out a way to keep him away from Phir S\textoverline{e}.  It fits with Dispatch's idea of sticking to the plan.''



``Why don't we press the offensive?''  Grace asked.  She still sat astride her bike.



``Believe me, I \emph{really} want to press the offensive,'' I said, ``But I don't want to get close to him while he's glowing like that.  That would be a pretty good reason unto itself.''



``He won't be using the radiation forever,'' Tecton observed.



``There's another key reason,'' I said.  ``Our guys are scared, maybe a little desperate.  It's not a good mindset for fighting.''



The heroes turned to look at the others, who had apparently taken our stopping as an excuse to tend to other business.  Golem had stopped to raise some hands, more lightning rods between us and the Endbringer, and others were flanking him.  The Y\`{a}ngb\v{a}n were looking after their injured.



``Desperate,'' Exalt said, gazing at the rank and file troops.



I wanted to join the others, to get involved and help, offer what little medical care I could, and the mental and emotional support I knew they needed, but we needed a greater direction, a mission.  I turned my attention back to Exalt.  ``Regent was desperate, maybe, and he died.  I'm scared that our side would take risks or put themselves in danger if we ordered them back into the fight.  This is getting uglier by the minute, and we're prone to doing stupid shit if we're backed into a corner, or if we feel like we need to end this fast so our friends can get the medical help they need.  Let's get the medical help, catch our breath.''



``There're more capes joining the fight now,'' Grace said.  I wasn't sure if that was a rejection of my plan or an agreement.  I followed her gaze to see a torrent of flames making its way in Behemoth's general direction.  A cape was hurling fireballs with some sort of space-warping effect tied to them, so they swelled dramatically in size with each second they were airborne.



I assumed it would be to Behemoth's \emph{advantage}, to have access to that kind of flame, but he wasn't deflecting them.  The fire exploded through the area around him, and I could see him lose his grip on a building as he reeled from the impact, slumped down to a place below the distant skyline of damaged and half-collapsed buildings.  Orange light lit up the area around him, marking the areas that had been set on fire.



The fireball hurler, barely visible as a speck against a backdrop of black-brown smoke, stopped abruptly.



``Why'd he stop?'' I wondered aloud.



``The radiation?''  Grace offered.



``The radiation was there before he went on the offensive,'' I said.  ``I don't see Behemoth retaliating, but the cape stopped lobbing fireballs.''



My bugs noted Eidolon's descent.  I turned around to see him depositing Rachel on the ground.  She shrugged out of his grip without so much as a `thanks'.



``He went underground,'' Eidolon informed us.



``He ran?  It's over?''



``No,'' Eidolon said.  He didn't elaborate as he watched Rachel back away and whistle to call her dogs.  The opaque pane of his mask was heavily shrouded beneath the heavy hood he wore, a dim blue-green glow emanating from within.  He was burned, his costume scorched and shredded in places, but the body armor beneath had more or less held.  Shaped to give the illusion that he had more muscle than he did, it seemed.  I could see blood running along the cracks at one panel of armor, where he'd apparently sustained a heavy blow.  He was mortal, after all.  Eidolon could bleed.



Fitting, that he layered disguises behind disguises.  Regent had done the same thing, to a lesser degree, had worn armor behind the deceptively light and delicate shirts he'd worn, had padding beneath his masks to cushion any blows, had hid a taser in his scepter.



I felt a pang of guilt, a swelling lump in my throat.  I'd never really gotten to know Regent, not to the extent that I'd gotten to know the others.  He hadn't really revealed much about himself, either.  I'd reminisced before about the intimacy of friendships, about the sharing of vulnerabilities, allowing others to be close, exposing oneself to possible harm.  I'd done it with Emma, back in the day, and I'd suffered for it.  I'd allowed myself to form a kind of intimacy with the Undersiders, and it might well have been a reason we'd survived this far.  Regent hadn't established that kind of intimacy with us.



Except maybe for Imp.



He'd hidden so much.  I'd only glimpsed the seriously disordered personality that lurked beneath the outer image of the lazy, disaffected teenager, had only seen traces of that part of him that just didn't \emph{care} that he could enslave a person's body and leave their mind as little more than a helpless observer.  And beneath \emph{that }aspect of himself, he'd had something else, something that had driven him to distract Behemoth so Imp might live.



My eyes fell on Eidolon.  Was there a similarity to Regent?  Lies, deception, a false face behind a false face behind a false face?



What was at the core?



Eidolon turned away from his observations of Behemoth, and he briefly met my eyes.



I felt intimidated, despite myself, but I didn't look away.



``Alexandria,'' I said, ``How is she--''



And he took off, not even waiting for me to finish.



``--still alive?'' I finished.



``I don't like him,'' Rachel commented.



``Nobody does,'' Dispatch said.  Rachel seemed to accept that with a measure of satisfaction.



``And why won't \emph{this} motherfucker die?'' Rachel asked, looking towards Behemoth.



``He's been fighting us for twenty years and he hasn't died yet,'' I said.



``So?''



``So\ldots he's tough,'' I said.  It was hard to answer a question so\ldots what was the word?  Innocent?  Guileless?



``We're tough.  Let's fuck him up.''



``I was arguing for that,'' Grace said.



\emph{Oh great.  They're of like mind}.



``But,'' Tecton cut in, turning his head her way, ``Skitter had a good reason as to why we \emph{shouldn't}.  We need to recover, recuperate.  Other heroes are picking up the slack, applying some pressure.  Or they were until he burrowed,''



Rachel snorted.  ``We do the chain thing again, cut him in half at the middle instead.  Or cut off his head.''



``Honestly?'' I spoke up, ``I'm not sure he'd die if we cut off his head.  And correct me if I'm wrong, but he could go after the people that carry the chain.  Even if it's someone like Eidolon, he could overheat and melt the part they're holding on to.''



``You're really a buzzkill,'' Grace said.



I didn't deny it.  ``There's one more reason we should go, though.  He's going to--''



\emph{Retaliate}.



Behemoth rose from beneath the ground a distance away.  In a heartbeat, things shifted from a near-quiet to chaos.  He was still glowing, and his claws crackled with electricity as he struck quickly, violently, and indiscriminately.



Three capes taken down, struck out of the sky by the bolts of electricity.  Even if they'd survived that much, the kill aura and the radiation would end them.



He turned, facing us, but the Wards were already moving, their wheels squealing on the pavement before they peeled away.



\emph{It's the Endbringer's pattern.  We hurt them or stall them enough, they change tactics, hit us back.}



``Go!'' I shouted.



Rachel moved, climbing astride her dog in an instant.  She whistled for her other dogs, directing them to Imp, Parian, Foil and Citrine.



Golem's hands absorbed some of the lightning that crackled around us.  Not one stream, but a \emph{storm}, with Behemoth at the eye of it.



And he was \emph{standing}.  He didn't necessarily have a full leg, but he had the ability to stand upright, now.



And Rachel, as I saw her making her way to the Undersiders, looked \emph{determined}.



Was it weird that she seemed more comfortable in the here and now than she had before the fight started?  It wasn't that she didn't look \emph{scared}, I could see the way her entire body was rigid, her hands clenched, white knuckled.  But she had a role here, she fit into a dynamic.



We took off, moving behind cover, running, as Behemoth crashed through a line of buildings.  Heroes from even half a mile away were lobbing attacks, and the stray shots that missed the Endbringer crashed down around us, tearing through buildings, turning stone to liquid, igniting nonflammable materials, one doing little damage but detonating so violently with the impact that my mounted teammates were nearly thrown free.



Behemoth roared, and I could see the Wards and Undersiders suffering.  A dog shook its head in an attempt to shake off the noise, and lost its sense of direction.  It crashed into a bike and sprawled.  Parian, Foil and Grace were dismounted.  Grace landed on her feet and physically ran, reaching for Tecton's outstretched gauntlet.  He extended a piledriver to give her something to hold onto.



Few bugs had managed to keep up, much less the ones with wires, but I brought a curtain between us and Behemoth.  I was past the point where I wanted to conserve them.  If it was lightning, I could only hope that Golem's makeshift lightning rods and my wires would protect us.



But it was flame.  It sheared through my swarm, and it splashed down around Parian, Foil and the dog.



The Endbringer had more aim than I'd expected.  He wasn't blind, despite the fact that his eye socket was empty.  But he wasn't entirely on target otherwise.  Was he relying on another sense?



The Y\`{a}ngb\v{a}n intercepted the attack, raising forcefields.  Parian did something with her thread, slapping the dog's hindquarters, and it bolted.  They were carried off, tied to its side, a flame still burning on Parian's sleeve and the hem of her dress.



Someone, an Indian cape capable of getting inside Behemoth's kill aura, closed the distance, and Behemoth was momentarily distracted by orange cords that bound his head, lashing him to the cape.  With that, the others had a chance to escape.



``Regroup!'' I called out, as I descended to the midst of the Undersiders and Wards.  ``I'll point the way!''



The sound of the fighting stopped with a crash.  Where was the motherfucker?  I rose higher to check, but saw neither Behemoth nor the cape who'd been binding him.  He'd burrowed.



It was \emph{quiet,} all of a sudden\emph{, }if not quite silent.  The defending capes were spreading out, and were hovering in place or holding positions, rather than bombarding the landscape.  The lightning and fire had stopped, and no shockwaves ripped through the city.  The rumbling was intermittent, mild when it wasn't almost imperceptible.  The ringing in my ears was louder than the ambient noise.



This was his new tactic, burrowing, surfacing.  But where was the retaliation?  Their whole damn pattern centered around repaying us twice over for any abuse we inflicted on them.



The armband crackled, and I jumped, despite myself.  The first message didn't come through the static, but the second was clearer.  ``\emph{Be advised, seismic activity suggests the Endbringer is still local.  Regroup and form defensive lines.}''



I did a little mental math, then pressed the button on my armband.  ``Armband, note that Behemoth may have a likely target, roughly eight to fifteen miles north-northwest of India Gate.''



At least, that was my best guess, judging by the flight speeds Defiant had noted for my flight pack and the time it had taken me to travel.



Every armband in earshot repeated my message.



``Keep going!'' I called out.  ``Keep moving!''



Surely he couldn't keep up with us while moving underground.  I didn't want to underestimate his intelligence, but was he even capable of holding a grudge?



What was Behemoth really doing?



The travel was uneventful, uninterrupted and eerily quiet, as we made our way to our next destination.  Three times, we stopped to pick up wounded, fashioning another quick sled for the dogs to accommodate all of them.



We reached the temple and delivered the sled to the temple doors.  The Chicago Wards stopped to park their bikes off to one side.  I waited for the Y\`{a}ngb\v{a}n to gather, extending my range, before I reached out to Phir S\textoverline{e}.



``\emph{He's underground.  He may be coming for you},''  I informed him, speaking through my swarm.



``I assumed,'' Phir S\textoverline{e} responded.  ``Thank you.''



``\emph{You need to leave, soon}.''



``I have a way out.  I'll leave when trouble begins.  Could you rid me of the bugs?  When you leave them, they fly about me, and I cannot afford distractions.''



I hesitated, then removed the bugs, shifting them to nearby rooms and corridors.  I left only a pocket of them to communicate with.  ``\emph{Be safe.}''



``You as well, Weaver.  Thank you, for the cooperation.''



``\emph{Have you gained a bit of faith?}''



``Faith gained in this, perhaps, faith lost in another.''



``\emph{I know what you mean.}''



``Good bye.  If we both live, perhaps we talk again, in a less dangerous time.''



``\emph{Good bye},'' I responded.



I drove the remainder of my swarm from his chamber.  It once again became a blind spot, an emptiness in my power's range.



``You okay?'' Tecton asked, as he caught up with me.  He held Cuff in his heavy armored hands, as though she were a small child.



``Saying goodbye to a self-professed madman.  Is she okay?''



``She's breathing, but I can tell she's hurting.''



I nodded, glancing over my shoulder as the others caught up.  Bitch brought her dogs.



We entered the front door, and I saw the amassed capes within.  Innumerable teams, looking after their wounded, lacking in direction.  The temple interior had no benches, and bedding had been laid out flat on the ground, capes set down in rows.  Medical teams were scrambling to take care of them, and capes with first aid experience were hurrying to help.  Dispatch already had his costume jacket off, his sleeves rolled up, and his hands dirty, taking care of a cape in power armor.  Parian was sitting on a mattress, tearing at her sleeve to show the burn, with Foil and Citrine beside her.



I couldn't help but notice that more than half of the capes were covered in white sheets.  That wasn't counting the innumerable capes left lying dead in the streets, like we'd done with Regent.  Behemoth killed more easily than he wounded.



Clockblocker had fallen.  I looked for him in the crowd of injured.  I didn't see him.  Then again, I had my suspicions already.  This only helped justify them.



Too many others I needed to track, to watch for.  But I couldn't use my bugs, and the dust and smoke had desaturated the colors.  Blood, in other places, marred the colors further.



``Miss,'' a local man in white said, in an accented voice, ``You cannot bring these animals.''



He was talking to Rachel, who glowered in response.



``Leave the dogs outside,'' I said.



``I'm not leaving my fucking dogs,'' she said, her voice hard.



\emph{Damn it}.  My eyes roved over the crowd, but I couldn't see Grue or Tattletale.  I didn't want to use my bugs, not in a sterile environment.  It was left to me to rein her in some.



``You can come and look for Grue and Tattletale with me, or you can stay outside with the dogs.''



She scowled, and for a second, I thought she'd stride out of the doors.  Instead, she pointed, barking out orders, ``Out!  Go guard!''



The dogs filed out of the double doors of the temple.  I could see the man relax visibly.



\emph{Don't let Grue be dead.  Don't let Grue be dead, }I thought.  \emph{Tattletale was okay, she was okay the last time I saw her}.



``My friends, they were stable,'' I told the man in white.  I saw Tecton crossing the room to lay Cuff out on one of the thin mattresses, turned my attention back to the man.  ``They were here since a little while ago.  Where are they?''



``Stable?  They were better?''



``Mostly better.''



``Up,'' he said, pointing at the nearest stairwell.



I used my flight pack without thinking, to give myself extra speed as I headed to the stairs.  Rachel was just behind me, her boots thudding on the floor.



There were more wounded above, recuperating in a long, narrow room with beds on one side.  In a grim twist, like a reminder of how close they'd come to dying, the opposite side of the room had more mattresses on the floor, more bodies.



How many dead, all in all?  Fifteen in this room alone, placed side by side, their shoulders touching.



``Skitter,'' Grue said, as I approached. Tattletale stood at his bedside, her phone in hand.  There were no curtains here.  No privacy.  This was all improvised, care facilities hashed together with what the locals had on hand.  He still wore his helmet, but he had his jacket off.  He noted the arrival of the others.  ``Imp.  Bitch.''



``It's Weaver now,'' I corrected him.



``You'll--''



``I know,'' I said.  I looked at his arm.  The burned flesh had angry blisters.  ``You okay?''



A hand pushed at me, moving me out of the way.  Imp.  She approached her brother's bedside.



``Hey kid,'' he said.  Beside him, I could see Tattletale's reaction.  She was silent, silenced by the damage to her throat, but she communicated well enough, that she'd drawn the full conclusion from our presence.  Her eyes closed, her head lowered.  There was no smile on her face, as she heaved out a whistling sigh through the plastic tube taped to her throat-wound.



``Regent's dead,'' Imp said.



I could see Grue go still.



As if reminding us of the culprit, there was a distant rumble.  It grew steadily in intensity, then stopped abruptly.  As far as I could tell, with bugs spread out over the area within two thousand feet or so, the Endbringer wasn't moving any closer to us.



``I should have been there,'' Grue said.



``Yeah, well, you weren't,'' Imp retorted.



I put a hand on her shoulder.  She tried to knock it away, and I dug my fingers in as I refused to cooperate.  It must have hurt; my old costume's fingertips had clawed points.  She didn't say anything on the subject.



``No, Grue,'' I told him.  ``You want to feel bad?  That's allowed, but I forbid you from taking the actual \emph{blame} for this.''



``You can't do that,'' he said.  His voice was hard.  ``I'm team leader, not you.  I'm supposed to pick up the slack, remember?  I'm supposed to manage these guys.  So don't turn around and decide shit like this, when you \emph{left}.  \emph{I} dropped the ball.  \emph{I} didn't move fast enough, I got hurt, and because of that, I wasn't there to help, to lead.''



``You're not allowed to take the blame, because if you start, then I've got to own up to it too,'' I said.  ``I--''



My breath hitched.  It caught me off guard.  I had to stop and take a deep breath.



Staying calm, composed, with my words carefully measured out, I said, ``--I was \emph{there}, and there was nothing I could do.  And if you're saying you could have done better, I've got to think I could have too.  So I'll match you one for one on any guilt trips.''



He sighed, heavy.  ``\emph{Fuck}.''



``Fuck,'' Imp echoed him.



``Fuck,'' Rachel followed, from the entrance to the room, as if we were toasting Regent in our own messed up way.  Tattletale was nodding.



``\emph{Fuck},'' I agreed.



``Christ,'' Grue said.  ``What do you even say to that?  How\ldots how do you even pay your respects to a guy like him?''



``He was a jerk, and worse,'' I said.  I saw Imp bristle, but held on to her shoulder, ``And he died for Imp's sake.''



Grue looked startled at that, as much as one could look startled with an all-consuming costume like the one he wore.  Tattletale, beside him, was unfazed.  She frowned a little.



``Christ,'' he said, again.



``So maybe we respect him by respecting that.''



There was no response to that for a few seconds.



``Yeah,'' Imp said, her voice small.  ``I'm going to fucking kill his dad for him.''



``That's not what I meant,'' I said.  ``I meant we should remember the best part of him.''



``That part of him would've killed his dad too,'' Imp said.



I sighed.  I wouldn't win here.



I changed the subject, seeing how quiet Grue was.  ``You should know, Grue, we got ours back.  We hurt him.  Behemoth.''



Grue raised his head, meeting my eyes with the empty black eye sockets of his mask.



``The others will explain,'' I said.  I let my hand fall from Imp's shoulder.  ``You wouldn't believe how much I want to be an Undersider again, right this moment\ldots fuck me, I want to remember the guy, to reminisce.  But this isn't over, and I've got another team to help look after.''



``We'll--''  Grue started.  He stopped as some doctors came barreling in, wheeling in beds with unconscious capes.



``Out!'' one of them shouted at us.  ``No more visiting, there isn't room!''



``Asshole!'' Imp snarled, jumping out of the way as someone moved the bed beside Grue's, nearly sandwiching her between the two.



``\emph{Go},'' Grue ordered her.  ``Go irritate someone who isn't loaded with painkillers.''



``A way of remembering Regent?'' she asked, as if she were trying to be funny, but there was a break to her voice as she altered the pitch to make it a question.



``Exactly,'' he said.



``Fuck it,'' she said, under her breath.  ``Fuck it, fuck it.''



We left the room, with only Grue and Tattletale staying.  The three of us made our way down the stairs, Rachel just to my right.



I glanced over my shoulder at Imp.  Her head was lowered a fraction, her arms folded.  Her gaze was on the rows and columns of injured and dead capes in the main hall.



We hadn't brought Regent's body.  We'd left it lying in the streets, too busy trying to stay alive to collect it.  Was that what she was thinking about?



There was a rumble, with a shaking that affected the whole structure.  Something distant, beyond my power's range.  A heavy crash.  Somewhere in a northwesterly direction.



\emph{Phir S\textoverline{e}}, I thought.  Had that been his complex?



At the entrance to the temple, heroes were gathering.  Our last stand.  I could see the Chicago wards at one corner.  Tecton was talking to Wanton, who was on crutches.  Wanton's right arm ended in a stump at the elbow, bandaged with crimson on the end.



\emph{Bad luck}, I thought.



I joined Tecton, only to realize that Rachel had accompanied me.  I supposed she didn't have anywhere else to go.



Imp didn't either.  Another glance showed her lagging behind the group, clearly lost in thought.



I lowered my voice ``Rachel, maybe you can do me a favor?''



``Hm?''



I ordered my thoughts, then voiced them, ``Grue and Tattletale are too injured to help out.  I'm focused on other stuff, and Parian and Foil are looking after each other.  Can you keep an eye on Imp?''



Rachel made a face.  ``I thought you wanted me to \emph{do} something.''



``This is key,'' I said.  ``She needs someone to \emph{be} there, right now.  That's all.''



``I don't know what the fuck I'm supposed to do.  What if she gets\ldots?''



Rachel trailed off.  \emph{Emotional?}



``Support her,'' Tecton cut in.  I suppressed the urge to wince.  He went on, ``She's your teammate, right?''



``How the fuck do I \emph{support }someone?'' she asked.  ``Stupid.  Not my thing.''



``You--'' I started, but Tecton was already talking, his voice deeper, his conviction stronger.  Grace was listening in as well, now.



``\emph{Empathize},'' he said.



Rachel glowered at him, unimpressed.



He tried again, earnest, ``Okay, here's a cheat I learned in a leadership seminar.  It's called active listening.  Someone says something, a complaint, or a criticism, or they're excited about something that happened to them.  For a lot of us, our instinct is to offer a solution, or expand on an idea, to fix or \emph{offer} something.  The key is to think about how they're \emph{feeling}, be receptive to that, and parrot it back to them.  They just got a new car, and they're happy about it?  A simple `that's excellent' or `you must be so proud' works.  It leaves room for them to keep talking, to know you're listening.  For your teammate who just lost someone she obviously cared about, just recognizing that she's upset and she's \emph{right} to feel upset, that's enough.''



I opened my mouth to say something, but I couldn't even \emph{begin }to sum up how useless this advice was to Rachel in particular.



``That's retarded,'' Rachel told Tecton.



``It \emph{works.}  And I know Grace is going to say something to me about it, about it being fake or false, but the thing is, you do that, and you start to do it because it's \emph{genuine}, because you care about their feelings, or because--''



I cut him off.  ``Tecton.''



He fell silent, turning my way.



``We don't have time to get into anything complicated,'' I said.



``It's retarded anyways,'' Rachel added.



I turned to her.  ``Rachel, did you ever have a dog with a deep attachment to another person or dog?  Someone they lost, before they found their way to a shelter, or to you?  Where they were still dealing, after the fact?''



She gave me a one-shouldered shrug.



``How would you treat that dog?''  I asked.



``Dunno, depends on the dog.''



``Basically, though?  You'd just \emph{be} there, right?  Do that for Imp.  Stay close, make sure she doesn't run off, as much as that's even possible with her, and give her the benefit of your company without intruding into her space.  Make sure she has all of the basics, both in the near future and in the next few days.''



``Okay,'' Rachel said, frowning a little.



``I know it's not the easiest thing, but she's a teammate, all right?  It's what we do for our team.''



``Right.''



``And just like a dog that's had a recent bad experience might snap, bark or growl, you need to understand that she might do the same.  Only it'll probably take a different form.  She'll swear a lot.  She'll probably try to get a rise out of you, try to provoke you or someone else.  That's how Imp growls.''



Rachel didn't even offer me a monosyllabic response at that.  She frowned instead.



``Trust your instincts, Rachel.  You're smarter than you think, and your gut responses, the decisions you make on the fly, they're good ones.  Turning around and using the chain for a second cut, back there?  That was good.''



Anyone else might have accepted the praise with a smile, but her frown only deepened.



``How was your advice better than mine?'' Tecton asked.  He sounded a touch offended.



``Customized to the individual,'' Grace said.  ``Don't be a sore loser.''



``I'm not sore.  I'm just usually pretty good at this, and I got called retarded.''



``The \emph{advice} was called retarded,'' I said.  ``Don't worry about it.  I'll explain another day, if we make it through this.  How's Cuff?''



``Skin's badly burned, but the burn didn't go much further than that.  She'll have the most amazing scars, too.  No serious internal or mental damage, as far as we can tell, but her muscles convulsed so badly they broke a bone.''



I winced.



``She'll make it to tomorrow, provided this doesn't turn ugly,'' Tecton said.



I nodded.  I sensed a rumble.  I couldn't tell how distant the attack was.



Where the hell was the bastard?  I was a little caught off guard by how \emph{quiet} things had gone.  He was giving us a chance to regroup?  Or was he letting us gather, so he could take us all out at once?



``Don't suppose you can sense seismic activity?'' I asked.



``Not with my suit.  My computers got toasted.  I'm running purely off the basics, and my intuitive understanding.  Stuff I reinforced, so I wouldn't get trapped in my suit like I did with Shatterbird.''



I nodded.



``Generally, though?''



``He's taking his time.''



If he was massing his strength for one good retaliatory hit, how would he do it?



Volcanos?  Earthquake?



``Let's go,'' I said.



``Go?''



``I've got a bad feeling,'' I said.  I turned to look for Rachel, saw her a distance away, her arms folded as she stood beside Imp.  They were looking at the sea of injured capes.  ``Rachel!''



I saw her attention snap to me.



``Go!  Get your dogs!''  I said.  I turned to the Chicago Wards, ``Wards!  Bikes!''



``You're serious,'' Tecton said.



``Everything I know about Endbringers, about basic parahuman psychology, it demands retaliation.  What's he done so far?  Saturated an area in radiation?  Thrown a few lightning bolts around?''



``You're expecting worse.''



``I've been waiting for the other shoe to drop.  Go.  Spread out.  We might need to respond to an attack on another location, with no time to spare.''



Tecton nodded.  He turned to his Wards, ``Go!''



I pushed my way through the gathered crowd.  I could see Defiant, with Dragon beside him.



``Weaver,'' he said.  ``Dragon says that was you, with the blast.''



I shook my head.  ``I helped coordinate, nothing more.''



``You hurt him.''



``\emph{We} hurt him.  And he's burrowed.  He's looking for a target, and I can't think of a better place for him to hit than \emph{this}.''



``We'd be able to put up a fight.  We have defensive lines.''



``Probably,'' I agreed.  ``But my guys are moving out anyways.  We've never done this much damage to him, and yet he's sticking around.  What I'm wondering is, \emph{why}?''



Defiant glanced at Dragon, then spoke.  ``He's--''



The ground shuddered.  Again, as before, the rumbling intensified.



This time, it didn't stop.  It got worse with every passing second.



``Reinforce!''  A cape hollered.  Someone else took up the call in an Indian language.  Hindi?  Punjabi?



I could see Annex flowing into the entryway, soaring through the wall's surface to the ceiling.  Golem created his hands, protecting the rows and columns of injured capes.



There was a press as the bodies flowed out the door.  I used my flight pack to fly over their heads, but even then, I bumped shoulders with others who could fly.  I wanted to help, but there was little I could do inside.



Eidolon and Alexandria had arrived at the building.  Eidolon touched the exterior wall, and an emerald green glow started to surround the structure.



The rumbling reached the point where capes were unable to keep their balance.  I raised off the ground, but the movement of the \emph{air} in response to the shuddering was enough to make me sway.



\emph{Tattletale.  Grue.  Parian.}



Behemoth emerged with a plume of gray-brown smoke, and the landscape \emph{shattered}.  It was Tecton's natural power, taken to an extreme.  Fissures lanced out in every direction and disappeared into each horizon.  \emph{Secondary} fissures\emph{ }crossed between each of the major ones, like the threads of a spider's web.



As far as the eye could see in every direction, terrain shifted.  Hillsides abruptly tilted, standing structures fell like collapsing houses of cards.



A full quarter of the temple collapsed.  The bugs I'd kept to the edges of the room could sense it as a small share of the capes who were in the entry hall were caught beneath the falling rubble.  The ones furthest towards the back.  Eidolon's protective effect kept the remainder intact.



Behemoth emerged from the smoke.  He was more robust than he had been, but that wasn't saying much.  Seventy percent burned away, perhaps.  The regeneration had slowed, but it was still functioning to a degree.  He'd recuperated, built his strength, and he'd used the time to, what?  Burrow through strategic areas?  Had the distant rumbles been controlled detonations or collapses at key areas?



The temple was the one building that stood.  Everywhere else, there was devastation.



How many refugees had just died, with this?  How many had stayed within their homes, rather than try to evacuate?



I felt hollow inside, just standing there, stunned, trying to take it all in.  The area around us was still settling, sections of land tilting and sliding like sinking battleships sliding into the water.



How many of us were left?  Seventy?  Eighty?  How many of them were hurt, exhausted, their resources spent?  Could we even coordinate, with so many of us speaking different languages?



``Last stand!'' a male cape I didn't know hollered the words, his voice ragged with fear and emotion.



Behemoth, three or four hundred feet away, responded to the shout with a lightning strike.  Our capes were too slow to erect barriers, and the protection insufficient.  Capes died.  For the first time, I averted my eyes.  I didn't want to know how bad the casualties were.  Our numbers were too thin.



I saw our Protectorate, what remained of it, stepping forward to form our defensive line.  Our \emph{last} defensive line.  The major ones, the ones I'd been introduced to, too many had died, or were injured.  These were unfamiliar faces.  The ones who were second in command, if that.



Eidolon landed to one side.  The Triumvirate had often posed in that classic `v' formation, with Legend in front, Alexandria to his left, Eidolon to the right, the lesser members in the wings, Eidolon was now apart from the rest of the group.  His cape didn't billow, his posture was slightly slumped.  He was tired, on his last legs.



There were murmurs as Alexandria advanced from within the temple.  Unlike so many of us, she didn't flinch as Behemoth struck out with lightning, the barriers holding this time.  Golem had raised lightning rods on either side of the road, fingers splayed as if he could gesture for Behemoth to stop.



Alexandria found her way to the end of the crowd opposite Eidolon, to our far left.  Satyrical and the other Vegas capes followed her.  Only a small fraction of them remained.  Others had apparently been injured or killed in battle.



Alexandria glanced over our ranks, and her eyes moved right past me, not even recognizing me.  For the briefest instant, I met her eyes behind that steel helmet of hers, and I saw that one had a pink iris.



That answered my question, I supposed.  Pretender couldn't take over a corpse, but there was no reason for him to take over Alexandria if she was alive and well.  Cauldron had collected Pretender, and they had him controlling her because she was no longer of any use to them on her own.



Our side was busy getting sorted into groups, spreading out so he couldn't hurt too many of us at once.  We were finding our formations, as our toughest capes absorbed and redirected the lightning he was throwing in an almost experimental manner.  He changed tacks, throwing flame, and a team composed entirely of pyrokinetics caught and redirected it with a concerted effort.  I backed away, and found Tecton at my back, with the remaining Chicago Wards.  Bitch stood just off to one side, her dogs ready.



One structure among several hundred thousand still stood, and our adversary was wounded, though undiminished.  Our ranks had been thinned in the most violent ways possible, through fire and lightning and a roar that could render organs to mush.  We weren't stronger than we'd been at the start of all of this.  I couldn't even say that the weak had been thinned out, or that we'd been united through hardship or loss.  Behemoth had picked off some of the strongest of us, and the trust between our factions was thin at best, with some eyeing the Y\`{a}ngb\v{a}n, others watching Satyrical's contingent.  We were just \emph{less}.



``Hold the line,'' Exalt called out.  Other capes translated for him, echoing his words with only a few seconds of delay, in four or five different languages.  ``We defend until the ones inside can be evacuated, and then we leave.  There's nothing left to protect here.''



A thin heroism, but that was heroic, wasn't it?  Protecting the wounded, defending the ones who'd put everything on the line to stop this monster.



If this was all a kind of microcosm for the world at large, that small heroism had to count for \emph{something}.  I wanted it to so badly I \emph{ached} for it.



Behemoth roared, and the last engagement opened.





