





Hero ushered him into the headquarters.  ``This is the last one.  I'd like you all to meet Chevalier.''



There was a chorus of replies.  Mumbled greetings with one \emph{exceedingly }enthusiastic response from a girl in the crowd.  It was almost mocking.



Chevalier ventured inside, a touch hesitant.  Not \emph{afraid}.  He'd told himself he'd never be afraid again.  No.  But this was unfamiliar territory.  The others were difficult to read.  Nine youths.



His eyes roved over the group.  Five girls, four boys.  His addition made it an even split.  Intentional?



The costumes ran the gamut from professional to homemade.  They varied in the degree of color, in seriousness, in combat readiness.  There was a boy, also, who had a professional looking costume, black and green.  It was a costume that had no doubt cost money, with leather and a utility belt, a leaf emblem over his heart.  Around him, Chevalier could see a vague nimbus, as though he could see only the brightest and darkest parts of some landscape that the boy stood within.  It was a subtle thing, an image that Chevalier could make out in the same way his perspective on something might alter if he had only his left eye closed, as opposed to his right.



A girl beside the boy with the leaf costume wore a less expensive looking costume, but she'd apparently gravitated towards him, a hopeful lackey or a romantic interest.  In the same way that the forest seemed to hang in the periphery of the boy, an older woman loomed just behind the girl.  She was kindly in appearance, like a next door neighbor, with hands burned black from fingertip to elbow.  The old woman was moving her lips as though she were talking, but the image was silent.



He started to turn his head, but the image changed.  The effect ran over the girl's skin, as though she were standing right in front of a glacier, the light refracting off of it.



No, the black hands on the older woman\ldots a result of fire?  Magma.



The girl caught him looking at her and frowned a little.  He averted his gaze.  She likely thought he was staring for other reasons.



At the far end of the scale, opposite the two professional, serious looking young heroes, there was a girl with a shield and sword.  Her helmet sat on the table beside her, a homemade piece of equipment with ridiculous mouse ears at the sides.  It wasn't a great helmet either; it didn't offer enough peripheral vision, was more decorative than protective.  She stood off to one side, but two others had gathered near her.  She was grinning, the one who'd stood out from the rest with her over the top welcome.



And the images, the glimmers, they showed the mouse-ears girl laughing.  For her companions, there was a strange writing system patterned on one boy's skin, and the other boy swirled with a smoke that wasn't there.



The images weren't an unfamiliar thing, but this was the first time he'd been confronted with so many in one place.  It was distracting, unnerving.



What were they supposed to be, the glimmers?



The remaining two members of the group were a boy, a clear vigilante of the night in appearance, with a costume that was black from head to toe, and a girl dressed in urban camouflage.  Chevalier's attention fell on the girl; her white and gray jacket was short enough that it didn't reach the small of her back, a blue tank top with a shield emblem on the front.  Her scarf, a complimenting shade of blue, was wrapped around her lower face, bearing the same emblem.  She sat in a chair, elbows on her knees, toying with a knife.



Odd as it was, she was \emph{more} grim than the boy who was \emph{trying} to look dark and disturbing.



``Take a seat,'' Hero said.  He laid a gentle hand on Chevalier's shoulder.



Such a minor thing, but it felt somehow critical.  What clique did he identify with?  What direction would he take?



He glanced over the rest of the group, at the images that had changed, and his eyes fell on the one with the knife.



In that instant, the knife disappeared, and there was a \emph{flare}.  The images were suddenly distinct, glaring, an image appearing in a flash, so brief he might have missed it.  A cluster of children, blood, their faces stark with fear and in one case, pain.



It faded as quickly as it had appeared, and the girl held a gun, now.



She'd caught him looking.  Meeting his eyes, she changed it again.



The image that flickered was of her, holding a gun with a silencer on the end, pointing it.  Her expression was one of desperation.



She'd changed the gun for a machete, apparently unaware.



He made his way across the room, and seated himself in the chair beside her.  She didn't even glance his way, her attention on the weapon as she ran her thumb alongside the flat of the blade.



``Army girl doesn't even speak english, you know,'' the boy in the nice costume said.



``She speaks some,'' Hero said.  ``It's fine.''



``I'm just saying,'' the boy said.



``I think we all know what you're saying,'' Hero answered.  ``You've made arguments about what you want the team to be, your desire to be taken seriously.''



Chevalier watched the exchange carefully.  His eyes fell on the figure behind Hero, and he tried to focus his attention on it.  It moved with glacial slowness, a four-legged creature with legs so long that the `window' around Hero didn't even show its main body.  Finger-like appendages at the base of each leg carved diagrams and ideas into the `soil' beneath as it walked.



``We've got the serious part down,'' the girl with the mouse ears said.  She drew her sword, thrusting it into the air, ``Huzzah!''



``So bogus,'' was the mumbled response.  ``As if her group has the majority.''



``I'm sure you'll figure it out,'' Hero said.  ``A lot of you have been through a lot, and some of you have only just \emph{stopped}.  Stopped running, stopped fighting, stopped dealing with a long series of crises.''



Hero's eyes briefly fell on Chevalier.  Chevalier lowered his eyes to the floor.



``The important thing to remember,'' Hero said, ``is that you've got \emph{time}.  You have time to figure out who you want to become, time to figure out what this \emph{team} will become, time to breathe.  To be kids again.''



Hero paused, glancing over the room.  He sighed.  ``And you have zero interest in that, I'm sure.  You're in a hurry to grow up, to be heroes.''



``You'd better believe it, boss,'' the mouse girl said.



``Just be careful,'' Legend said, as he strode into the room.  He was accompanied by Eidolon and Alexandria.  ``This is about training, not thrusting you into the midst of trouble.''



``That comes later,'' the mouse girl said.



``If you decide you want it,'' Legend answered.



The sheer presence of the heroes here was changing the energy of the room.  The listless teenagers had perked up.  They were paying more attention, more alert.



It was no longer one more act in a long sequence of hoops and events.  This was the main capes of the Protectorate, all here in one place, for \emph{them}.



``Well,'' Hero said, clapping his hands together.  ``I'm not good at the formalities.  Being in charge isn't my thing, as much as those three like forcing the job on me.  So what do you say?  Let's crack open the soda bottles, cut the cake and celebrate our inaugural Wards team.''



The mouse girl's team cheered and whooped.  Nobody else really joined in with even half of the enthusiasm, but there was more of a response than there might have been before the rest of the Protectorate had showed up.  Chevalier even allowed himself a cheer, joining in with the clapping.



It \emph{was} exciting.  Exciting and a little scary.  Like stepping out over a chasm.



As the others made their way to the table, Chevalier stood from his chair, then glanced down at the army girl.  ``You want cake?''



She raised her head.  ``Yes.''



``What do you want to drink?  I think there's cola, ginger ale, sprite\ldots''



``The brown drink,'' she said.



``Coke, then.''



He left her sitting in the chair, paying far too much attention to her weapon, and grabbed two paper plates.



``I'm curious why you sat next to Hannah,'' Hero commented, as he served himself some cake.



Chevalier glanced at the girl with the weapons.  He felt uncomfortable, ``People are making it a bigger deal than it is.  It was just me sitting down.  I didn't put much thought into it.''



``Maybe,'' Hero said.  He laid a hand on Chevalier's shoulder.  ``But it's good that you did.  She could use a friend.  Might make a world of difference, in the long run.''



Chevalier shrugged, stepping up to the tray and placing a slice of cake on each plate.



``We're all ignoring the \emph{obvious} reason,'' the girl with the mouse ears said, getting in Chevalier's way as she reached for a plastic fork.  ``He thinks she's hot.  He wants the \emph{poontang.}''



Hero cleared his throat in a very deliberate way.



``Don't be juvenile,'' the leaf-boy told her, from the front of the line.



Chevalier shifted awkwardly.  The girl with the mouse ears was in his way, and he couldn't move down the table to get a drink.  She wouldn't budge until this was resolved.



``I got the vibe she and I are similar,'' Chevalier said.  It was honest.  The images he'd seen, of the girl\ldots



And it was apparently the wrong thing to say, because mouse-ears was only more insistent, now.  She smiled, cooing the word, ``\emph{Similar}?''



``You didn't figure it out yet?  Chevalier's the vigilante that went after the Snatchers,'' the leaf-boy said.



Hero turned around, and his voice was a little hard, ``Reed.  That's not your story to share.''



``It's okay,'' Chevalier said.  ``They'd find out eventually.''



Mouse-girl looked confused.  ``The Snatchers?  Are they supervillains?''



``No,'' Chevalier said.  He used the distraction to push past her and get to the area where the two-liter bottles of soda were lined up.  He poured the drinks for himself and Hannah.  ``They were ordinary people.  Bad people, but ordinary.  Except maybe the leader.''



``Maybe?''  Mouse girl asked.



``I didn't give him a chance to show me.''



Her eyes widened.



Chevalier felt strangely calm as he spoke, ``Not like that.  Alexandria caught up with me at the very end.  When I was trying to decide what I'd do with him.  She told me she'd stand by and let me kill the guy, if I really had to, but I'd go to jail afterwards.  That, or I could come with her.  Come \emph{here}.''



Hero frowned, glancing at Alexandria, who had gathered at one corner of the room with Eidolon and Legend.  They were looking at the kids, talking, smiling.  ``I'm glad you made the right choice.''



Chevalier shrugged.  \emph{I'm not sure I did}.



He was still angry.  Still hurt.  His little brother's absence was still a void in his life.



``Maybe now you can stop asking questions,'' Reed told the mouse girl.



``Never!''



Reed sighed.



``Everyone has their baggage,'' Hero said.  ``Sometimes it's in the past, sometimes it's in the present, other times it's fears for the future.  But this is a fresh start, understand?  I'm pretty mellow, believe it or not, but I'm going to be upset if I hear that anyone's holding any of that stuff against a teammate, or if you're letting it hold you back.  Understand?  This is a second chance for everyone.  You're here to \emph{support} one another.''



There were silent nods from Chevalier, Reed and the mouse girl.



``Good.  Now go.  Eat cake, drink soda, be merry.  And when the party is done and us \emph{adults} are gone, with you kids left to your own devices, check the empty room, the one that isn't assigned to any of you.  I stocked you guys with video games and movies.''



``No way,'' Reed said, smiling genuinely for what might have been the first time.



``Yes way,'' Hero said, returning the smile.  ``But we're not going to tell the higher-ups, are we?  It's a bit of a secret, and you don't betray that secret by letting yourself slack on the training or the schoolwork, right?''



Reed's smile dropped a little in intensity, but he nodded.



``Go on,'' Hero said, still smiling,  ``And don't get me in trouble.''



Reed hurried back to his chair, as if getting there sooner meant the party would end earlier, speeding up his access to the treasure trove Hero had hinted at.



Wordless, Chevalier managed the drinks and two plates as he carried them over to Hannah.  He gave her a plate and a cup, and she smiled without thanking him.



``A toast,'' Alexandria said, stepping forward.  ``To the first Wards team of America.''



``To second chances,'' Hero said.



``A brighter future,'' Eidolon added.



``And to making good memories,'' Legend finished.



``Memories,'' Hannah said, under her breath, nearly inaudible as the room clapped and cheered.  She was looking down at the machete that she'd placed across her lap, the paper plate with the cake balanced on the flat of the blade.



Chevalier didn't respond.  His eyes were on the phantom images, barely visible.



\blacksquare



The screen displayed the list.  Chevalier scrolled down, his expression grim.



Marun Field, December 13th, 1992.  Behemoth.
S\~{a}o Paulo, July 6th, 1993.  Behemoth.
New York, March 26th, 1994.  Behemoth.
Jakarta, November 1st, 1994.  Behemoth.
Moscow, June 18th, 1995.  Behemoth.
Johannesburg, January 3rd, 1996.  Behemoth.
Oslo, June 9th, 1996.  Leviathan.
Cologne, November 6th, 1996.  Behemoth.
Busan, April 23rd, 1997.  Leviathan.
Buenos Aires, September 30th, 1997.  Behemoth.
Sydney, January 18th, 1998.  Leviathan.
Jinzhou, July 3rd, 1998.  Behemoth.
Madrid, December 25th, 1998.  Leviathan.
Ankara, July 21st, 1999.  Behemoth.
Kyushu, November 2nd, 1999.  Leviathan.
Lyon, April 10th, 2000.  Behemoth.
Naples, September 16th, 2000.  Leviathan.
Vanderhoof, February 25th, 2001.  Behemoth.
Hyderabad, July 6th, 2001.  Leviathan.
Lagos, December 6th, 2001.  Behemoth.
Shanghai, April 23rd, 2002.  Leviathan.
Bogot\'{a}, August 20th, 2002.  Behemoth.
Lausanne, December 30th, 2002.  Simurgh.
Seattle, April 1st, 2003.  Leviathan.
London, August 12th, 2003.  Simurgh.
Lyon, October 3rd, 2003.  Behemoth.



``Stop,'' Chevalier ordered.  The artificial intelligence halted the scrolling.  The scroll bar wasn't even at the halfway mark.



\emph{Brighter future indeed}.



He rubbed at his eyes, suddenly feeling very weary.  Nothing worked out like it was supposed to.  The Wards were supposed to be a safe haven for teenaged capes, buying them time to prepare themselves, to train and figure out what they needed to figure out.  Somewhere along the line, some Wards had joined the fight.  Locals, defending their homes, naturally.



As the ranks of adult capes were whittled down, more had attended the fights, as if unconsciously acknowledging the need, or as if they were under a subtle pressure to do so.  Just like that, the ideals and ideas that had helped form the original Wards team had eroded away.



He swept a hand in front of him, and the ship read the gesture, a new image appearing on the monitor.  The two screens on either side showed Behemoth's attack on the city.  He hadn't ventured far from where he'd emerged.



Chevalier only glanced at the screens from moment to moment, his focus more on the infrastructure, the resources at his disposal.



San Diego, absent.  They'd lost too many members, abandoned by those who'd lost faith in the Protectorate, with the remnants cannibalized to support other teams in need.  San Diego was more or less stable, so there'd been little pressure to resupply them with new members.



Except that Spire, San Diego's team leader, hadn't felt confident walking into the fight.  There'd been the human element, the fears, the concerns.  He'd had cold feet at the last second, decided not to come.  An integral part of their defense, gone, forcing them to adapt.



There were so many elements like that.  Little things.  He'd heard so many complain about how the Protectorate handled the attacks.  How they were disorganized, inefficient.



Maybe he'd shared in that sentiment, to a degree.  That had changed when he'd participated in his first fight, when he'd seen just what it meant to be in the fray, against an enemy that couldn't truly be stopped.  But still, he'd harbored doubts.



Then he'd taken command of a team, and he'd seen the process of trial and error, as they learned their opponents' capabilities, saw how Leviathan or the Simurgh could keep tricks up their sleeves for \emph{years}, before using them at a critical moment.  Even now, they didn't fully understand the Simurgh's power, how long it might take someone to recover, if recovery was even possible.



And now he led the attack.



He drew in a deep breath, then exhaled.



\emph{Focus on the present}.  He'd lose it if he dwelled on the pressures, on the fact that every attack to date was another added pressure, a set of losses to avenge, a step towards mankind's fall.



Vegas was absent too.  They'd turned traitor, walked away.  Satyrical had turned down the offer for a ride to the battle, claiming they'd make their own way.  It was disconcerting, to think they had access to transportation in that vein.  Teleporters?  A craft that could and \emph{would} carry people halfway around the world fast enough?  Disconcerting to think they had access to resources like that so soon after defecting.



But not surprising.



Brockton Bay, in large part, was sitting this one out.  Hannah wasn't a true asset against Behemoth.  Besides, the truce was in worse shape than it had been even in the beginning, and the portal too important.



He allowed himself a moment to think of Hannah.  They'd dated briefly, then separated.  It had been a high school romance, and they'd both been too busy to really pursue things.  What had been one or two dates a week became \emph{maybes}, then had ceased to happen at all.  He'd graduated to the Protectorate, changed cities, and they hadn't said a word on the subject.



Chevalier had seen her grow, though.  That was what he kept in mind to assuage his disappointment over the way things had gone.  She'd come into her own, confident, intelligent.



In a way, he was glad she wasn't coming.



He turned around to face Rime and Exalt.  He could see the shadows, as he now thought of them.  Rime's younger self accompanied her, sitting on the bench beside her, arms folded around her knees, face hidden.  The real Rime was sitting on the bench, a fold-out table in front of her, a laptop open.



And Exalt?  His `shadow' was barely visible, impossible to make out.  When it came to the fore, though, Chevalier knew it would look much as Hannah's power did in its transitions.  Phantom images.



He'd raised the subject of the images with others.  When his proximity to Eidolon had started to give him migraines, he'd confessed about the images.  He'd feared a kind of schizophrenia, but Eidolon had reassured him otherwise.



It was a piece of the puzzle, but that puzzle was still far from complete.  Until they had more to work with, it was merely data.  Glimmers of memories and dreams, the conclusion had been, after long discussions with Eidolon and the parahuman researchers.  An effect of the thinker power required to manage his own ability, tied to trigger events in some fashion.



Except now he was wondering if he'd been misled.  Eidolon was a traitor, one working for a group that clearly had some deeper understanding of powers.  Maybe it had been in Cauldron's interests for Eidolon to \emph{lie} about this.



``Record numbers.  Lots of capes are coming,'' he said.  Rime and Exalt both looked up.



``But\ldots'' Exalt said.  He seemed to reconsider before finishing his sentence.



``But we're disorganized,'' Chevalier finished it for him.  ``People we should be able to count on are gone.  Plans we had are falling apart because those people aren't there.



Exalt nodded.



``PRT wants us to play this up,'' Chevalier said, ``I'm supposed to involve you guys in leadership aspect of things.  If you're willing, I'm not going to dwell on it.''



Exalt arched an eyebrow.



``You're team leaders.  You've got the experience, at least to a degree.  But I don't want to dwell on peripheral stuff.  We're focused on the fight?  All right?''



Rime and Exalt nodded.



``I'll lob a few of you some softball questions, then we get right to it.''



``Right,'' Rime said.



The ship altered course, Chevalier felt his heart drop.  Silkroad's power wasn't giving them any forward momentum anymore.  They were close.  Landing in a minute.



``You ready for this?  Being leader for the first time?''  Exalt asked.



``No.  Not for one this important.  Everyone who's paying attention knows this is a crucial one.  Maybe even the point of no return.  We lose this, we lose New Delhi, and there's no going back.  We'll never get to the point where we can consistently beat those motherfuckers, never recoup what we've lost.  I screw up here, and the world will know.''



``They can't blame you,'' Rime said.



``They damn well can,'' Chevalier retorted.



She frowned.



The ship descended, four legs absorbing the impact of the landing almost flawlessly.



He turned to the swords, set into the floor of the craft.  There were two.



In truth, there were three.  The largest was thirty feet long, running from the ramp at the back to the cabin at the front, almost entirely set into the floor.  There was no decoration on it.  Only mass, sturdy craftsmanship, and the mechanisms necessary for the cannon that was set inside the handle and blade.



It would have been too heavy for the ship to carry, except he'd already used his power, drawing it together with a second blade, an aluminum blade a mere four feet long.  Lightweight.



His ability to see the `shadows' about people was an extension of this power.  He could see the general makeup of the two weapons, the phantom images, the underlying physics, in lines and shapes and patterns.



It was about perspectives.  Relationships.  He'd drawn them into one blade, with the appearance of the larger, the properties of the smaller.



The third blade was decorative, with a ceramic blade, gold and silver embellishments and inlays in the blade.  The thing was ten feet long from end to end, and again, it had the cannon set within.   Combining the first blade with this one proved more difficult.  He granted the weapon the appearance of this blade, gave it the cutting edge, but retained the lightweight mass and the durability of the largest weapon.



Fine balances.  He adjusted it, tuning its size for convenience's sake.  The heft remained the same, as did the effective weight as it extended to the rest of the world.



His armor was the same, only it was too large to bring on the craft.  A veritable mountain of construction grade steel, as light as aluminum, with the decoration of a third set.  It had required some concentration, to maintain the balances he'd set, but he was confident he could fight outside of the kill aura's range.



He glanced at Rime and Exalt, then nodded.



The ramp opened, and the three of them emerged.  There were heavy thuds and the sound of metal striking metal as the other ships landed, forming a ring, with the doors and ramps pointing inward.  A fortification to guard the arriving heroes.



The Protectorate and Wards teams were gathering, with a degree of organization.  His new Protectorate had gathered into the general positions they held at the conference table.  Rime to his left, Exalt to his right, their teams behind them.



And he couldn't help but notice the gaps.  San Diego, Vegas, Brockton Bay.  Three of the more prominent teams in the United States.



Defiant, Dragon and Weaver were among the last to arrive.  They joined the unofficial capes who'd filled the void that should have been occupied by the San Diego capes.



``The ships have all arrived,'' Chevalier said, breaking the silence, starting his speech.



\blacksquare



It was only after the Y\`{a}ngb\v{a}n were out of sight that Chevalier could breathe a sigh of relief.



``You know your roles,'' he said, to the capes who remained  He searched the rooftop, and found who he was looking for.  ``Mr. Keene, walk with me.''



The dark-skinned man nodded assent, falling in stride.  He wore a neat suit with a PRT pin, official identification on a lanyard around his neck.  Morgan Keene was the PRT's liaison and ambassador to unofficial teams across the world.  Chevalier could see the glimmer of a power there, suppressed but there.



The fact that the man was a parahuman employee of the PRT wasn't so unusual.  The fact that it was a well-kept secret \emph{was}.  The power was out of sync, however, which was stranger still.  Since Chevalier had chanced to make Morgan Keene's acquaintance, years ago, the man's shadow had changed.  The core elements were the same, but the appearance of it had changed enough that he'd wondered if the man had managed a second trigger event.  He would have assumed so, except there was no intensity to corroborate the idea.



It left him suspicious, but it wasn't a suspicion he could act on.  In an ideal world, Chevalier hoped to replace Mr. Keene.  In reality, the situation was too chaotic, and Morgan Keene too entrenched in things.



``You're upset about the Y\`{a}ngb\v{a}n.''



``I don't like surprises.''



``I sent you a number of emails, three voice messages.''



``Can we trust them?''



``No.  But they're still an asset.  Alexandria wanted them on board.  When you installed your new administration, they said to keep going.''



Chevalier sighed.



``Our thinkers are on board to advise with the concentrated defense.  I've coordinated the foreign capes, Arbiter's handling some of the translations.''



``Okay.  And our\ldots less legitimate thinkers?''



``Accord and Tattletale.''



``Yes.''



``Rime set them up with access to the PRT databases.  Connection is slow but remains strong.''



Chevalier nodded.  ``I'll talk to them.''



``Of course,'' Mr. Keene answered.



Chevalier made his way to the downstairs room.  He paused at the entrance.



Tattletale's `shadow' peered around with a dozen eyes all at once, each set different in design, in appearance and apparent function.  A mosaic.  Accord's was a glimmer of an old computer, the edge of a desk that wasn't there.



It wasn't as meaningful as it had appeared to be at first.  They were only figments of ideas that had been codified and collected in times of stress.  Ideas imprinted on a malleable surface during trigger events, or moments when trigger events had been on the verge of occurring.  As an individual's power waxed and waned, the images grew more distinct, shifted between the images personal to the cape in question, and the stranger, dream-like aspects that seemed to relate to the powers.



``Accord.  Tattletale.  Do you have something constructive to offer?''



``Yep,'' Tattletale said.



``Your defensive lines are a disaster waiting to happen,'' Accord said.



``Straight to the point,'' Tattletale commented.



``A disaster?'' Chevalier asked.



``I'm wondering if you've done this on purpose,'' Accord stated.  His eye moved critically over Chevalier.  ``You're going to fight the Endbringer in a melee.''



``Yes,'' Chevalier said.



``And you've picked the new Protectorate team with the idea that they would support you.  The core team is all ranged.''



``Yes,'' Chevalier said.



``Ego?'' Tattletale asked.



Chevalier shook his head, then thought for a moment.  ``Perhaps.''



``Well, ego's a part of the job.  Question is, can you live up to it?''



``I can try.  But more than anything, I'm not going to put people on the front line if I'm not willing to go there myself.''



``Foolish,'' Accord said.  ``Everyone has their place in the grand scheme of things.  You do yourself and \emph{everyone else} a disservice if you try to put yourself where you don't belong.''



Chevalier shook his head, but he didn't reply.  There would be no convincing this one.



Accord continued, ``There are only two ways you could make this plan work.  The first would be using a sword long enough to reach past his Manton effect bypass, the second is to somehow within that range and survive.''



``Accounted for,'' Chevalier said, a touch irritated.  He didn't need this.  Not now.



``Usher,'' Tattletale supplied.



``Ah.  I see,'' Accord said.  ``And if Usher were to be struck down by a chance lightning bolt?''



``We have fallback plans.''



Accord shook his head.  ``I'll develop better.''



Chevalier grit his teeth.



``I'm watching him fight,'' Tattletale said, ``And something's off.  I've been watching old videos of the Endbringer fights, looking over maps, and it doesn't fit together.''



``What doesn't?''



Her finger tapped hard on the map she'd printed out.  ``Location, pacing.  They're \emph{toying} with us.  Acting.''



``You're crediting them with more intelligence than they have.''



``Are you telling me that because you \emph{really} think they're dumb, or because you don't want to-``



Chevalier could sense the attacker by the movement of the shadows.  He whirled around, only to find himself face to face with a cloud of the `shadows'.



The Y\`{a}ngb\v{a}n, one of them.



An assassin?



He couldn't even make out the figure, behind the layers of images.  Glimpses of twenty, thirty, \emph{forty} trigger events.



Defying the truce, here?  Now?



He felt his anger stirring.  He adjusted the balances of his blade, maintaining the reach, the appearance, but he altered its interaction with the rest of the world, maintaining its lightweight feel as far as \emph{he} was concerned, changing it in other respects.



``You lunatic!''



He had his sword out in a flash, swung.  A forcefield appeared, but the weapon breezed through it as if it weren't even there.



It was, in all respects except appearance, and the ease with which he moved it, a weapon that weighed upwards of fifty tons, as durable as the heaviest weapon.  The cutting edge of the ceramic blade.



His opponent slipped out of the way, and images flared with life as he drew on a power to fly.



Chevalier couldn't make him out in the midst of the shadows.  Did the Y\`{a}ngb\v{a}n know this would trip him up, slow him down?



It didn't matter.  The attacker didn't have offensive strength.  Two more attacks failed to penetrate Chevalier's armor.  He advanced, swung, thrusted, and his opponent stepped back, narrowly dodging.



Chevalier pulled the trigger, but a power flared and the shot jammed in the chamber.



\emph{Can't afford to expend resources on this.  Have to prepare for the fight}.



He followed up with more swings.  Each missed by a hair.  His opponent was scared, frantic.



And suddenly his opponent was a distance away.  The images, the movement of the clouds outside, telltale signs of being stopped in time.



He advanced, felt another attack fail to penetrate his defenses.  Again, time stopped, his opponent used the window of opportunity to back away.



In between the following two pauses, he could see Accord and Tattletale change places, moving to the door, now barred with a forcefield.



They'd have to hold their own.  Chevalier assessed his opponent, as best as he could, through the storm of hellish images.  Each of them was fractured, broken.  Nothing to be gleaned from them.



But the opponent was sloppy.  Letting him get dangerously close between resets.  It was a question of letting him make a mistake, occupying his attention, so the thinkers would be safe.  A chess game, moving the knight to keep the king in checkmate.  There was only so much space in the room, and he could position himself to force the Y\`{a}ngb\v{a}n member to move further, to have less time to act, leaving more room for a mistake.



``No,'' he could hear Accord murmuring, the word barely above a whisper.  He chanced a glance at the pair.  Tattletale had a hand on her holster, and Accord had stopped her.



He didn't get a chance to see anything further.  He felt the strength go out of his lower body, a slow but incredible pain tearing through his midsection.



The laser.  How?



He had only a moment to adjust the balances in his power, so the blade and armor wouldn't crash through the floor and tear down half of the building.



\blacksquare



\emph{I missed the fight}, he realized, as he woke in a hospital bed.



The ground rumbled violently.  He looked up to see Tattletale in the corner of the room, half of her attention on what was happening outside the window, the other half on a phone.



``He's here?''



She turned to him, tapped her throat.  He could see the tube in her throat.



He sighed.



She approached the bedside, attention on the phone.  She held it out for him to read.



A notepad executable read:



hes here.  defenses crumbled in a minute.  rime dead.  melted off more than half his outer body and he still fighting.  last stand to protect hosp'l for evac and he cutting them down



Chevalier shut his eyes.  \emph{We lost}.



Tattletale was already typing again.  Her expression was grim as she focused on the phone.



He tried to sit up, and found himself unable.  It was a pain concentrated in one area, but it was so immense that made his entire body react.  His ears buzzed, his vision wavered, and every muscle clenched, as he lay there, trying to ride it out.



She showed him the phone as he lay there, panting.



he still at full strength.  shouldn't be.  he's an onion, inner rings progressively tougher.  next 15% way tougher than rest combined.



``I know this,'' he gasped out the words.  He moved the sheet to examine himself.  His breastplate had been removed, and his stomach had fresh incisions on it, with sutures holding them closed.



How long had he been out?



She showed him her phone again.



they stapled your gut up.  if outer body is like this then why does he have it?  useless.



He reached up to swat the phone away, felt a pull on his stomach and winced instead.  He knocked it out of the way with his other hand.  Still painful, but easier.



She drew it out of his reach, started typing again.



He turned himself over in the bed, nearly retching at the intensity of the pain, but he found himself on his side.  Even at the weight of aluminum, the armor on his legs and hands was heavy enough to help weigh him down, hold him in position.



She offered him a hand as he swung his legs down, trying to use the momentum to sit up.  He nearly fell, but she caught him, dropping the phone onto the bed in her haste to help him stay sitting upright.



His chest heaved, and he growled out each breath.  The growling helped, on a primal level, but that wasn't saying much.  Just sitting upright was bad enough that he thought he might pass out.



``My breastplate.''



She handed him the phone, then crossed the room to where a bundle of belongings were gathered on a chair.  They'd cut off the layer of mesh that sat beneath the armor, and the cloth that sat against his skin.  She discarded each of those and simply brought him the armor.



It had held its form.  Good.  He glanced at the phone.



outer body is cosmetc only.  why?  because he supposed to scare us.  behemoth was fashioned.  unnatural life.



She brought the front portion of the armor, resting it on the corner of the bed.  She tapped the phone.



``I read it,'' he growled.  ``Help me put it on.''



She tapped the phone again.



``It doesn't matter,'' he said.  ``It won't change the outcome of this fight.''



She nodded agreement, then lifted the armor, bringing it to his chest.



There was a crash outside, a chorus of screams.  Chevalier grit his teeth.



``Back piece,'' he said.  She gave him a pointed look.



``Please,'' he added, growling the word.



She turned on her heel, crossing the room to pick up the armor, slowly, almost leisurely, as she typed on the phone with one hand.  She held the armor in the other as she made her way back, then took several damnable seconds typing out the message before putting the phone down.



``We don't have time for your typing,'' he said.



She only gave him a level, silent stare, as she moved the rear portion of the armor into place.  He reached for the clasps, but moving his left arm was too painful, pulling on the muscles of his stomach.  He used his right for what he could, then waited for her to finish.



Indian doctors rushed down the hall, pushing beds on wheels, four in a row.



He conceded to pick up the phone and read what she'd typed.



they regen slower as damage is further from center.  simurgh core not in human body.  decoy.  prob in join of biggest wing instead.  Is why body fragile n slow to heal.



His eyes widened.  ``We destroy the center, we destroy him?''



She gave him a look as if he'd just asked if the sky was green, incredulous.  She shook her head.



``Why the hell not?''



She just shook her head.



``I don't know why the hell not. Where's his center?''



She pointed with two fingers, at her collarbone.  The base of the throat, between the shoulders.  Quite possibly the deepest set part of his body.



``Help me stand.''



The entire building rumbled.  For a moment, he thought the entire point would be rendered moot as the structure collapsed.



It took three tries to get him to his feet, with him holding a shelf on the wall with his right hand, her leveraging her entire body's strength with her shoulder under his armpit.  He stumbled forward, catching himself on the shelf, and heaved for breath, feeling the strength threaten to leave his legs with every deep inhalation and exhalation.



But he couldn't.  Couldn't allow himself to.



Tattletale was pulling on a blue latex glove.  He watched her as she reached out and placed a hand on the space beside the incisions, where the burn had been patched up.



``What are you doing?''



She reached for the phone.



no tear inside u.



``I could've told you that.''



She shrugged, her eyes on the screen, thumbs typing on the onscreen keyboard.  She raised the phone.



can try.  prob wont work.  dense enough 2 fuck wit time n space there.



``Right,'' he said.  ``My Cannonblade?''



She sighed, making her way to the end of the room.  She collected his Cannonblade from the floor by the chair.  He'd made it as light as it could go in every respect, before he'd passed out.  Even so, moving his left arm to try to hold it made him seize up in agony.



For now, he was a one-armed fighter.  He gripped the handle in his right hand, then exerted his power.  He could \emph{see} it grow heavier, even as the weight remained effectively the same in his hand.



He rested it against one shoulder, then managed a limping step forward.  He very nearly fell.



Another step.



He focused on his power, as a way to distract himself, planting one foot in front of the other, the armor squeaking in one point where a knee joint had bent as he'd fallen after fighting the Y\`{a}ngb\v{a}n assassin.  It was easier to keep moving than to stop and start again, so he moved forward with an almost machinelike rhythm, limping.



He'd never forgive himself if they lost this fight and he didn't even \emph{fight}.



Stairs.  He had to make his way down.  One mistake, a faltering step, and he'd collapse.  He'd probably be unable to stand, if it didn't tear his stomach apart.



He made his way down, the stitches pulling against the fresh incisions with every step.



The building shuddered.  His mind a fog of pain, he reached out for the railing for stability, only to remember he was holding his sword.  It plowed through railing as if it were a meticulous sandcastle, raining pieces on the ground below.



He swayed, and for the briefest moment, he considered that it might be easier to fall.  Easier than making it down the next ten steps.  If there was a ten percent chance his stomach stayed intact, a twenty percent chance someone could help him stand\ldots



But he took another step down, and somewhere in the midst of planting his foot, he found his balance.



Everywhere, doctors were struggling to evacuate.  Some capes were working to help, even injured ones trying to pull things together.  Still fifty or sixty capes to evacuate.



And the bodies\ldots people who had died because he'd failed them.  Because he hadn't been able to defeat the assassin, to take his role at the front of the battle lines, where he could bait Behemoth into the various traps they'd laid.



He had to suppress the guilt.  There would be time for blame, self-directed or otherwise, later.  He'd bury the mental pain like he was with the physical.



\emph{This is how Behemoth fights.  Indomitable.  Never slowing.  Always progressing forward}, Chevalier thought.



He could remember who he'd once been.  So long ago.  Well before he'd had his first of twenty fights against the Endbringers.  Before meeting Hannah and the rest of the original Wards.



They'd been in a car crash, in the middle of a vacation.  Strangers had stepped in, crowding the car to help his little brother out, while his parents were reeling, moaning in pain.  They'd tried to get him out too, but he'd been pinned, the car handle had been scraped away in the collision, the interior handle protected by the child locks.  They'd left, and for hours, as the emergency services arrived and the rescue continued, he'd wondered why.  He'd triggered, caught in the wreckage, but had been too insensate to do anything about it, to even realize the full gravity of what had happened in the midst of the chaos.



It was only later that he found out they were serial kidnappers.  The crash that had broken his mother's leg in three places had been orchestrated.  So had the collection of his little brother.



Three years later, when he heard about the group again, he put together a makeshift club and armor and set about hunting them down.  He appeared in the news in the midst of tracking down the individual members, and again and again, they had described him as relentless, to the point that it had very nearly became his codename.  Revenge had been all he had left.



Then, just as he was now, he'd been fueled by anger, by pain.  He could barely see, as black spots blotted his vision.  Revenge, again, was his only option, only it was the end point, rather than the beginning.



\emph{I told myself I'd never let myself be afraid again}, he thought.



His left hand was nearly useless, so he hit the double doors at the front of the temple with his sword instead.  Wood splintered as the doors parted.  He trudged forward, ignoring the doors as they swung shut, bouncing off his armor.



\emph{Record numbers show up, and this is all that's left}?



Barely fifty heroes still stood their ground.  The back lines were sheltered by giant hands of stone, Hellhound's mutant dogs collecting the wounded, carrying them around the side of the building.  Eidolon and Alexandria wrestled with the Endbringer, fighting in close quarters against the monster.



\emph{Alexandria}?



He shook his head, nearly losing his balance as he continued his forward march.  He could barely see straight, and it wasn't helped by the phantom images that riddled the mass of capes.  Images he had called glimmers when he was a youth, that he called shadows now that he was an adult.



But Behemoth\ldots the Endbringer was little more than a skeleton with extensive padding.  He'd never seen this much damage delivered.



Chevalier focused his power on his blade, making it as large as he could.  He continued marching forward.  There was no indication Usher was okay.  Rime was dead, and he had little idea about the state of the supporting forces who'd been intended to help him attack, who'd \emph{trained }to assist him.



He extended his blade towards Behemoth, using it to gauge the distance for the kill aura.  Defending capes cleared out of his way as he walked forward, between two of the stone hands.  The shadow of his sword was warning enough.



One of Behemoth's legs seemed less developed than the other, the toes missing, the bones less pronounced, the flesh thinner.  He reached the perimeter and slammed the weapon down into the earth with his one usable arm.



His steam nearly spent, he collapsed over the handle of the weapon, his hand still gripping the handle, and he pulled the trigger.



The size of the weapon and the effect of the firing pin seemed to help with the jammed mechanism.  That, or the transition to being closer to his largest blade had shifted something in a fractional way.  The shot blasted Behemoth in the calf of his weaker leg, and the Endbringer fell.



Again, he pulled the trigger, over and over.  Three, four, \emph{five} shots.



He stopped before he spent the sixth.



He'd dealt damage, but it was precious little.  Flesh had torn at the leg, not quite as dense as it should be, by all reports.  Had the regeneration not finished rebuilding the complete structures?



Rendered effectively one-legged again, Behemoth crawled forward on three limbs.  Alexandria struck him from above, driving him face first into the ground.



Why was she here?  She was supposed to be functionally dead.



Chevalier could feel a sensation crawling through his body, an energy.  It didn't invigorate, not on its own, but he could feel a kind of relief.



Usher was alive, and Usher's power coursed through him.  With luck, he'd be immune to Behemoth's power, or at least partially immune.  Nobody had received the benefit of Usher's ability and been brave enough to venture into Behemoth's kill range.



Chevalier pulled his sword from the ground, swayed, and very fell over.



Defiant caught him.



\emph{Old friend}, Chevalier thought, though he didn't have the breath to speak.



Anyone else might have spoken up, told him he didn't have to do this, that it was madness.



Defiant was silent, supporting Chevalier, helping him right himself.  Defiant understood this much.  The need, the \emph{drive}.



Chevalier took his first step with Defiant's help.  The second was only partially supported.  The third was on his own.



He closed into the kill area, and he could feel the heat touch him.  It heated the armor, but didn't reach him.  Usher's power at work.  He tried to inhale, and found no air.  Choking, he forced his mouth shut.



Holding his breath, Chevalier brought the sword down on Behemoth's shoulder, a blow from above much like Alexandria had delivered, followed by another.



His aim wasn't good, the blows off target.  If his form were better, he'd be landing each strike in the same place, time after time.  Not so, with the blade this big, the margin for error so great.



With that in mind, Chevalier shrunk his sword as he closed the distance, shut his eyes as lightning crackled around the Endbringer.  With the scale smaller, the effective edge was that much sharper.  The blade bit just a fraction deeper each time.



He couldn't stop walking without falling, couldn't stop swinging the weapon in the same rote motion without risking that he'd never be able to raise it again, however light it might be.



His goal was the spot Tattletale had mentioned.  The core.



Behemoth swiped at him, but he was already shifting the balance of his armor, moving to block the blow with the flat of the blade.  The sound of the impact was deafening, and it wasn't something Usher's power protected against.  But Usher's power was finnicky at best.  Unreliable.



At the very least, it was holding up here.



He found a measure of strength, then swung the cannonblade, driving it for the deepest part of the wound.



Behemoth lurched, changing position, and the painstakingly created notch in his shoulder shifted well out of Chevalier's reach.  He let up on the intense heat, turned to radiation instead.  Heroes scrambled to retreat from the ominous glow.



\emph{Bastard, }Chevalier swore.  He released a sound somewhere between a moan and a groan, exhaling the last of the air in his lungs, greedily sucking in air.



Something flew past him, shearing straight through Behemoth's chest.  A wheel of metal, thin, with two bars sticking out of the center.  It cut through the Endbringer like he wasn't even there.



Dazed, lungs fit to burst as he held his breath, barely coherent, Chevalier turned.  He saw Tecton with his piledrivers extended, Weaver just behind him, along with two of the new Wards: the white supremacist's child they'd picked up in Boston and a boy in a white cloak.  They stood all the way at the back lines of the battlefield, by the temple, along with a character he didn't recognize.  A girl in black.



His eyes settled on Weaver, surrounded by the nimbus of her power, which glowed with an intensity that surpassed any and all of her teammates.  When she stepped forward, it was like she was pushing against a curtain, only it was a membrane, a network of individual cells, each with tendrils extending out, so thin he couldn't make them out, except by the highlights that seemed to rush down them as she gave conscious direction to her bugs.



\emph{Second chances}, Chevalier thought back to his inauguration to the Wards.  He'd harbored doubts about taking her on board, but memories of that day had been a factor.  He'd needed a second chance.  So had Hannah.



Colin, even, though it came much later.



It was a good feeling, to see that coming into play.  He knew she wasn't all the way there, but she'd taken a step forward.



It was a \emph{better} feeling to watch as Behemoth's shoulder shifted, attached by a mere \emph{hair}.  The weapon had cut through his ribs, torn through the space where his heart should be.



\emph{That'll do}.



Alexandria hit him, and the arm came free.  Behemoth lurched, planting his one remaining hand on the ground, and came just short of collapsing on top of Chevalier.  He was only a few feet away, glowing with the radiation.



\emph{I'm dead}, Chevalier thought, without a trace of the despair he'd imagined he would feel.



He tried to move, to raise his blade, only to find his armor refusing to cooperate.  It had melted, the joints and joins flowing into one another.  His sword wasn't much better.  The ceramic properties he'd applied to the edge were heat-resistant, but the remainder of the weapon were growing more nebulous in shape, the hottest parts of the metal flowing down to obscure the edge.



He concentrated, and found his power beyond his reach.  Too tired, his stamina gone.



Trapped in a hot wreck of metal, an explosive death just a short distance away.  It had been his starting point, and it had been the end.



It would be the optimal time for a second trigger event, the thought passed through his thoughts.



Of course, the joke went that you couldn't get a trigger event by \emph{trying }to have one, so even \emph{thinking} about a second trigger event was enough to banish any possibility.



Not so funny, in this moment.



His power worked best with \emph{similar} things.  Differences made it slower.  It was why he had the same firing mechanism at the core of each of the three weapons he used for his Cannonblade.



Now, as the battle raged around him, he was nearly blind with the visor of his helmet melting, at his utter limit in terms of stamina and pain tolerance.  Behemoth delivered a shockwave, and Usher's power protected him, his boots welded to the ground kept him from falling over.



He reached for his power, grasping at his armor, and he didn't reach for anything familiar or similar.  He reached for anything, everything.  The ground, the \emph{soil, }\emph{air}.



Somewhere in the midst of that desperate struggle, he found his armor coming apart.  He wasn't even \emph{willing} it, not even forming any coherent idea of what he was doing, but his power operated of its own accord.



Free of the armor, he could move his weapon.  It was slag, barely a sword anymore, but the core still had some density to it.



He made it grow.



He made the sword grow, from ten to twenty feet in length.  It was more by the growth than by any action on Chevalier's part that it extended into the wound.  The weapon penetrated into the scar Weaver's crew had created, as close to the core as Chevalier could get it.



He made it grow to its greatest possible length, a full thirty feet, his head turned skyward to the monster that glowed silver and black.



Space and time distortion were supposed to protect it?  He'd fight fire with fire.



Flesh parted as the blade grew inside the wound.  He put his finger on the trigger, ready to fire.



Before he could, the sword's tip touched the core, and everything went wrong.



His power abruptly ceased to take effect, and the blades came apart, in its three individual pieces.  They slid from the wound, falling down around him.



Behemoth lurched forward, and his wounded leg struck Chevalier, knocking him to the ground.  He could feel the gunshot break of multiple ribs shattering.



Supine on the ground, unable to breathe, but for tiny pants, Chevalier stared at the sky, unwilling to look directly at the ensuing scene, even if he could have managed to turn his head.



There was a horrible crash as a sweep of one claw shattered the stone hands.  Glowing silver, he loomed over the defending capes, scorched and electrocuted those who'd fallen within his instant-kill range.  One of Hellhound's mutant dogs, \emph{Dragon}.  Others he couldn't make out in the midst of the clouds of dust.  Rendered to ash and melted armor in heartbeats.



They were the lucky ones, Chevalier thought.  The radiation was generally observed to be \emph{concentrated}, limited to a certain range, manipulated to strike only those within a hundred feet or so of Behemoth, to saturate the landscape and render it uninhabitable.  These capes were close enough.  Their deaths would be slow, painful.



A failure.  Hopefully the ones in the temple had been evacuated, and the capes at the rear of the battle line free to retreat.



The ground rumbled violently, churning and smoking.  Behemoth was burrowing.



The fight was over.



Chevalier stared up at the shifting smoke of the sky above, struggling to breathe, not entirely sure why he was bothering.  Maybe he wouldn't die of the radiation, thanks to Usher's power.



Long moments passed as the rumbling of the earth faded in intensity.  The air was still filled with the screams and shouts of the various capes and doctors fighting to save the wounded, the dull roars of distant helicopters, carrying the evacuated capes away.



Chevalier watched as the worst of the smoke cleared, and he imagined he might have seen the glowing blur of the sun through the clouds.



Not the sun.  It was a figure.  Scion.



He would have laughed if he could.



\emph{Too late}.



\emph{You showed up too late}.



Scion lowered himself to nearly ground level.  His golden hair moved in the wind as he gazed over the battlefield.  His white bodysuit was smudged here or there on the sleeves, but otherwise seemed so pristine that it seemed to \emph{glow} in the gloom.



No, part of that glow was real.  The faint light touched Chevalier, and he could feel his breathing ease.  It was reaching out to everyone present.



\emph{A consolation prize?  A bit of healing?  Maybe a helping hand against the radiation, for the others?}



He managed a soft laugh.  The glow was making the pain easier to handle.  He could almost breathe, now.



He closed his eyes, and he felt a tear roll down from the corner of his eye.  He suspected he wouldn't have been able to tear up without the healing.



Not sufficient to fix the broken bones, or the damage to his stomach, perhaps.  He opened his eyes to look at Scion, to ask a question.



But Scion was gone.



A noise rose up from those who remained in the crowd.  Gasps, cheers, shouts of surprise.



Chevalier forced himself to move, stared at the spear of golden light that had risen from the earth, just on the horizon.  Scion.



He held Behemoth in his grip, released the Endbringer to fall two or three hundred feet to the ground, struck his falling foe with a beam of golden light, as if to\emph{ shove} Behemoth into the ground.



Behemoth's lightning crackled between them, catching Scion, but the hero didn't even seem to flinch.  He hit Behemoth again, and this time the beam of energy didn't stop.  With virtually every structure leveled, there was nothing to hide their view but the lingering smoke and dust, and even that wasn't thick enough to hide the light.



The aftershock of it traveled across the city, quelling dust storms, blowing past the assembled heroes like a strong gust, faintly warm.  Even though the ray didn't reach quite that high, the clouds of smoke and dust parted visibly above Scion.



Chevalier watched, staring, belatedly thought to count how many seconds had passed.



\emph{One, two, three, four}\ldots



Behemoth generated a shockwave, but it was muted by the light, suppressed.



\emph{\ldotseight, nine, ten, eleven, twelve\ldots}



Behemoth's silhouette thrashed as he tried to move out from beneath the shaft of light, but Scion only reoriented the beam, keeping it fixed on his target.



\ldots\emph{sixteen, seventeen, eighteen, nineteen, twenty}, \emph{twenty-one}\ldots



The light ceased.  Behemoth was gone.  A plume of dust rose from the earth, at the very limits of their vision.



Scion plunged beneath the ground, heedless of the intervening terrain.



Again, Scion rose from a point beneath the shattered surface of the city.



Again, he held Behemoth in his hands.  Thinner than a skeleton, the Endbringer was little more than a stick figure from Chevalier's vantage point.



Only this time, with a flare of golden light to accompany the movement, he tore the Endbringer in two.  The legs came free of the pelvis as two individual pieces, and Scion obliterated them with a pulse of the golden light.  The air that reached the crowd of wounded heroes was cool, this time.



In Chevalier's peripheral vision, people were emerging from within the temple.  Chevalier didn't spare them a direct glance.  If he was seeing what he thought he was seeing, then he wouldn't take his eyes off the scene for anything.



Behemoth slammed his claw into the glowing hero, and the shockwave tore him free of Scion's grip.  Scion followed him with a glowing sphere of light, and Behemoth redirected his fall, generating an explosion in mid-air, hurling himself towards the assembled crowd.



Eidolon stopped him with a violet forcefield that spread across the sky, a solid obstacle to arrest Behemoth's momentum, stopping him dead in his tracks and leaving him suspended a hundred feet up in the air.  His one intact claw clutched the edge.



Scion followed up with another shaft of light, and the forcefield shattered in an instant.  Behemoth was slammed into the road, three streets down from the gathered heroes outside the temple.



The Endbringer glowed, and the swelling light was too intense to look at.



Just seeing it, there was no question of what he was doing.  \emph{A final act of spite}.  Turning himself into a bomb.



A stream of darkness poured from one of the helicopters, filling the street Behemoth lay in.  For an instant, the Endbringer was almost entirely obscured.



Scion fired one more beam, and the darkness was obliterated, swept away.



The silhouette of the Endbringer flickered, then disintegrated.  There was no detonation, no destruction to the landscape.  Only the cleansing light.



The beam dissipated, but its effects hung in the air, canceling out noise, stilling the air.



Slowly, the crowd took up a cheer, a cry of victory from everyone with the breath to spare.



As noise returned to the landscape, the stilling effects of Scion's light fading, Chevalier closed his eyes, listening.  With the noise of the helicopters and distant fires mingling with the shouts and hollers of joy from the defending capes, he imagined he could hear the whole world cheering alongside them.





