





``Well bandaged.  They did a good job,'' the doctor had to raise her voice to be heard over the helicopter's rotors.  She was older, blond to the point that it was hard to distinguish if her hair was still blond or graying, her expression creased in concern.



Wanton nodded mutely.



``What happened?'' the doctor asked him.



``Falling debris,'' Tecton offered, from the other side of the helicopter.



The doctor nodded.  ``We'll leave it as it is.  The pain's okay?''



``Meds help,'' Wanton said.  ``Feel like I'm almost dreaming.  And I'm going to wake up, and none of this will have happened.''



``It happened,'' Tecton said.



``Why isn't everyone cheering and hollering anymore?''



``Really fucking tired,'' Grace said.  She was beside Cuff, who'd been stripped of her armor from the waist up, with only a thin covering of near-liquid metal on her upper body for modesty's sake.  A nurse was attending to her arm.



``Really tired,'' Golem said.  ``Oh my god.  My entire body hurts, and I didn't even take a direct hit.''



``The roars and shockwaves might have done internal damage,'' the doctor said.  ``You'll each need a CT scan and MRI.  Let me know if there's any acute pain.''



``I think it's more that I've never exercised this much in my life,'' Golem said.



``You'll hurt worse tomorrow,'' Grace commented.



``Damn.''



The doctor, for her part, turned her attention to Wanton.  ``We'll need to double-check for bone fragments when we get back to the hospital.  You'll need surgery.  Chances are good this was a rush job.''



``I\ldots my arm,'' Wanton said, lamely.



``I'm sorry,'' the doctor responded.



``No, it's like\ldots I should feel worse, but I don't.  Maybe it's the drugs, but I feel this rush, like I've never been so glad to be alive.  I'm \emph{pumped}.''



``You may be in shock,'' the doctor observed.



``We're \emph{all} in shock,'' Tecton said.



There were murmurs of agreement across the helicopter.



``Is anyone else a little freaked out?'' Cuff asked.



``Freaked out?'' the doctor asked.



Cuff shook her head, not responding.  Her attention had shifted to her arm, as the doctor bound it.



Tecton ventured a reply instead.  ``I think I understand what Cuff means.  It's hard to believe he's gone.  It's like, you're five years old, and Leviathan appears for the first time, and your parents have to explain that a bunch of people died, and it's because of these monsters and yet nobody has figured out \emph{why}.''



``Yeah,'' Cuff said.  ``What happens next?  Leviathan or the Simurgh?  We kill them?  Stop them from blowing up or doing their version of blowing up?  I can't really imagine that we'd beat them, give our all and hope that Scion shows up and fights like that again, kill them, and then have everything be okay.''



``You \emph{just }got powers, barely a month ago, and you're already this grim?'' Wanton asked.



``I've been dealing with the aftermath of the Endbringer attacks for a while,'' Cuff said.  Her eyes were on the floor, and an expression of pain crossed her face as the doctor cut away a tag of burned skin on her shoulder.  The scar was like a snowflake carved into the skin's surface, angry and red.  Her arm seemed to tremble involuntarily.



``It's okay to worry,'' Tecton said.  He gestured towards Weaver.  ``Weaver said as much.  They've got a nasty habit of escalating, in the fights themselves and in the grand scheme of things.  Behemoth got too predictable, so Leviathan started to show up.  We started to coordinate defenses, get the world on board to deal with them, Simurgh comes.''



``And now we killed one, so how do they escalate from there?'' Grace asked.



``It's a concern,'' Tecton said, ``And it's one that people all around the world are going to be discussing.  Rely on them.  Don't take the full weight of the world onto your shoulders.  We fought, you guys made a good show of it,'' Tecton said.



``I could've done more,'' Cuff said.



``You're \emph{new}.  Inexperienced, and I don't mean that in a bad way.  As far as jumping in with both feet first, you guys managed it.  You, Golem, Annex, you stood up there, shoulder to shoulder with veteran heroes, and you \emph{fought}, even though you're rookies.  You have absolutely nothing to be ashamed of, okay?''



Cuff didn't reply.



``Okay?'' Tecton asked.



``When my family got killed in Hawaii, I made promises to myself.  It's why I came.  I don't feel like I did enough, to fulfill my own end of those promises.''



``There's always next time,'' Tecton said.



``You say that like it's a good thing,'' Wanton said.



``Yeah.  \emph{Shit},'' Grace muttered.  ``It's not quite over yet, right?''



``Right,'' Tecton said.  ``But there's time before the next one.  Let people in the know handle the worrying.  We did everything we could.  Now we recuperate.  We celebrate, because was \emph{deserve} to.  We take the time to heal.''



In response to the glances cast his way, Wanton waved his stump around.  ``Going to take getting used to.  Getting dressed, eating\ldots''



He moved the stump in the direction of his lap, jerked it up and down.



Cuff looked and squeaked in embarrassment before averting her eyes.



``\ldotswriting,'' Wanton finished, a goofy smile on his face.



``Your handwriting must be \emph{awful},'' Golem said.



There were chuckles here and there from among the group.  Even the nurse tending to Cuff smiled.



``We did good,'' Tecton said.  ``And some people will recognize that.  Others are gonna see all the bad that happened in New Delhi and point fingers.  Be ready in case you fall under the crosshairs.''



There were nods from the rest of the Chicago Wards.



Tecton glanced at Weaver, then back to his team.  ``What do you think?''



``You have to ask?'' Grace asked.



``You weren't keen at the idea at first,'' Tecton replied.



``I'm still not, not a hundred percent.  But whatever little doubts I have, it's kind of a no-brainer.''



``Yep,'' Wanton said.



``Golem?''  Tecton asked.  ``Have you even talked to her about it?''



``I'm a little scared to,'' the boy said.  ``I mean\ldots''



He glanced at the doctor.



``Everything here is confidential,'' Tecton said.



``Well, given my past, the people I was with before I came here, I'm worried there's hard feelings.  They were in the same city.  I don't know what exactly happened.  What if one of them did something to Weaver or her friends?  Is she the type to hold a grudge?''



``Going by what apparently happened in Brockton Bay,'' Wanton said, ``Not so much.  If she has a reason to hold a grudge, you don't tend to live very long.''



Golem frowned.



``You're not being helpful, Wanton.  Or fair to Weaver,'' Tecton said.



``I'm \emph{suffering}, Tec,'' Wanton said, making the words into an exaggerated groan.



Tecton shook his head, turning to Golem.  ``Tell her.  Explain your circumstances, let her know you're from the same city, that you don't share your family's ideology.''



``The name should say as much,'' Golem said.



Tecton nodded.  He drew in a deep breath, then exhaled.  The adrenaline was burning off, and with it, a deep exhaustion was settling in.



He looked at Weaver, where she sat at the far end of the bench.  Her old teammate had insisted on coming with her, along with a small cluster of dogs.  They'd fallen asleep within two minutes of takeoff.  Weaver had been first, her head leaning against her friend's shoulder.  Her friend had been next to drift off, a dog in her lap, others lying underneath the bench.



``We'll talk to the bosses,'' Tecton said.  ``See about taking Weaver onto the team.''



\blacksquare



How was this supposed to work?



``Door me,'' Pretender said.



A light sliced across the floor of the alleyway, three feet across.  When it had reached its full length, it began thickening, raising up until the portal was a full four by seven feet.  There was a long white hallway on the other side.



Carefully, he stepped through, with legs that weren't his own.



``Pretender.''



He stopped, then turned around.  ``Satyr.''



``You don't have to go with them,'' Satyrical said.



``I think today proved I do.''



``And everything we were working on?  Everything we were working towards?''



``I talked to some powerful people.  People behind the scenes we've barely heard of,'' Pretender replied.  ``What we were working on in Vegas doesn't even compare.  Small potatoes.''



``Doesn't feel like small potatoes.  What's so important that you'd run off?''



Pretender frowned, an expression hidden by the helmet he wore.



``You can talk to me.  You \emph{know} I can keep secrets.  Or are you talking about the Endbringers?  I think today showed they can deal with Endbringers on their own,'' Satyr said.



``It's bigger things.  Bigger than Endbringers,'' Pretender answered.  ``End of the world.''



Satyrical sighed.  ``Of course it is.''



``I'll help you with the little things, when I have the time.  We have resources, and maybe we can use you guys.''



``Sounds like a plan,'' Satyr said.  He approached Pretender, extending a hand.



Pretender shook, gingerly, unsure of the full extent of Alexandria's enhanced strength.



Satyr held on to the hand, caressing it.  ``They say you should marry your best friend, and now that you're a woman\ldots''



Pretender chuckled a little before withdrawing his hand from Satyr's.  ``That line again?  I \emph{don't} think that's what they meant.''



``She's yours for keeps?''



``Brain dead.  Her body's peculiar.  Doesn't really age.  Hair doesn't grow, nails don't grow.  Wounds don't really heal or get worse.  She used cosmetics to look older, to throw people off.  Only the brain was left pliable, adaptable.  Even then, most of it was hardened, protected, those duties offloaded to her agent.''



Satyr studied Pretender's new body without shame.  His eyes rested on Pretender's forehead.  ``I see.  And with that plasticity, the brain was left more vulnerable.''



``Only a little.  Enough to be an Achilles heel.  She's a case fifty-three, I suppose.  All of us may be.''



``All Cauldron capes?''



Pretender nodded.  ``To some degree or another.''



Satyr seemed to take that into consideration, rubbing his chin.  When he spoke, though, he spoke of something else.  ``What you did\ldots you knew that they'd figured you out, and that I was next in line, that I'd get questioned too.  You killed her for my sake, to buy me time.''



``Are you mad?''



Satyr shook his head.  ``We've killed before.  Selfishly, selflessly.  Only difference is you got caught.''



``Well, I got away.''



``In a fashion, yes.  You got away,'' Satyr said.  ``You've even reached a higher position in life.''



``Wearing someone else's skin, living their life,'' Pretender replied.



``Yes, well, that was always going to be your fate, wasn't it?''



Pretender chuckled.  ``I've missed you, buddy.''



``Likewise, you freak of nature,'' Satyr responded.



``Just because we're doing different things now, it doesn't mean goodbye.''



``Good.''



``We stay in touch,'' Pretender said.  ``I'm sure my new group can use you, and you can draw on our resources, I'm sure.  Our goals are more or less aligned.  Only difference is scale.''



``Well then.  Good luck with saving the world.''



``And good luck with saving civilization from itself,'' Pretender answered.  He looked skyward for a moment.  ``Close the door.''



The portal closed.



\blacksquare



\strong{Connecting to ``agChat.ParahumansOnline016.par:6667'' (Attempt 1 of 55)}\strong{Resolving Host Name}\strong{Connecting\ldots}\strong{Connected.}\strong{Using identity} ``\strong{Iblis'', nick}``Iblis''
Welcome to Parahumans Online Chatroom #116, `The Holdout'.  \underline{Rules Here}.  Behave.\strong{Obey the @s}\strong{.}
Ryus: shorthand for seismic activity.  earthquakes.
Kriketz: any word on deaths yet
Divide: No word on deaths.  This is Behemoth.  It's normal to see a radio silence like this.  Divide: They can't report deaths because the armbands get knocked out.
Spiritskin:  Hi Iblis!\strong{Iblis}:  Word is first capes are returning home.
Aloha:  !
Loyal: Who?  Who?  Names!
Deimos: how is new delhi?
@Deadman@:  I'm in contact with main channel, can pass on details if you can verify.
@Deadman@:  PM me.\strong{Iblis}: Loyal – Not sure.\strong{Iblis}: Deimos – City hit bad.\strong{Iblis}: Deadman – Not sure how to verify.  Only have texts on phone.  Sending PM.
Poit: they made it
BadSamurai:  how bad?
Ultracut:  Poit nobodys saying they amde it
Poit: they stopped him or they wouldn't be leaving
Deimos: Nooooooo! new delhi hit bad?
Aloha:  X(\strong{Iblis}:  Texts I'm getting from cape-wife friend are saying Scion finished Behemoth off.\strong{Iblis: }Absolute annihilation.QwertyD: Troll
Groupies: no fucking way
Aloha: \texttt{O_o}\emph{Deimos is now known as Absolute Annihiliation}
@Deadman@: Verify now or ban.
Absolute Annihilation: fuck yea Scion!
Arcee: Omg wat?\strong{Iblis}: sending PM with texts.



\blacksquare



Colin shifted his weight restlessly, watching the screens.



There was a process, he knew.  He'd been filled in on the details, forewarned.  That didn't make this any easier.



Too many years he'd spent alone.  Too many years, he'd had nothing to care about.  Nothing and nobody to hold precious.  A dad who worked two jobs, a mother who traveled.  They'd divorced, and virtually nothing had changed in the grand scheme of things.  They'd looked after him, but they hadn't been there.  They had been occupied with other things, with dreams and aspirations that had never included him.



Colin knew he had been the weird child.  Had never made friends, had convinced himself he didn't want or need them.  He was efficient in how solitary he was.



He'd even prided himself on it, for a time, that there was nothing to hold him back.  That he could, should the mood strike him, pick up and leave at any time.  He'd modeled his life around it, had led a spare existence, devoid of the little touches of home, of \emph{roots}.  He'd saved money so he had the ability to travel, to get a new place in a new city if the mood struck.  It had even been an asset when he had joined the Protectorate, the ability to relocate, take any open position.



It was only now, a full fifteen years later, that he started to wonder what he'd missed out on.  Did most people know how to handle this sort of thing?  The absence of someone they cared about?  Did they have an easier time handling the moments when they weren't sure if they'd ever see those people again, or was it harder?



He'd altered Dragon's code.  It wasn't a tidy thing.  Tinker work rarely was.  There were too many factors to consider, and a tinker who didn't \emph{specialize} in a particular area would never be able to plumb the depths.  Too many things connected to other things, and the full extent of the connections was impossible to fathom in entirety.



At best, he could study each alteration as much as was possible, act in ways that could minimize the damage.



Every adjustment, even on the smallest levels, threatened to damage a dozen, a \emph{hundred} other areas.



And now he would find out if Dragon's backup would restore properly.



\strong{Error:} Temporal Modelling Node 08 has failed to load.  Attempting child routines to bridge.



\strong{Error:} Horospectral Analysis Node 1119 has failed to load.  Attempting child routines to bridge\ldots\strong{Successful Load:} Circadian Checkmatch Node ER089.  Require 2/3 more stable child routines for acceptable bridge.\strong{Error:} Metrological Chronostic Node Q1118 has failed to load.  Attempting child routines to bridge\ldots



\strong{Error:} Stimuli Tracking Node FQ has failed to load.  Attempting child routines to bridge.



\strong{Successful Load: }Orientation Patch Node FQ02903.  Require 3/3 stable child routines for acceptable bridge.\strong{Error}: Parietal Space Node FQ161178 has failed to load.  Attempting child routines to bridge\ldots\strong{Error: }Recognition Demesnes Node FQ299639 has failed to load.  Attempting child routines to bridge\ldots



He pulled off his helmet, setting it on the bench beneath the monitor.  He rubbed one hand across his head.  He'd taken to shaving it close, in part for the efficiency of it, in part because the surgeries to replace his eye and the implants he'd set into recesses in his skull had required incisions in his scalp.  Dragon had handled that.



His fingers traced the faint, almost imperceptible scars that ran neatly across the sides and top of his head.  Marks she'd left him.



More errors appeared on the screen.  The estimated time of a successful backup clicked upwards with each one.  \emph{Two hours.  Three hours.  Six hours.}



At the same time, in Colin's head, the odds of a successful load were going down.  \emph{Twenty-five percent.  Twenty three.  Fifteen.}



There were other backups.  He suspected the ones that had been uploaded after his tampering would run into the same issues.  The same errors.



The ones \emph{before}?  Before he'd altered anything?  It would be a different Dragon than the one he'd come to know.  She would watch the video feeds, listen to the tapes, even experience some of those things for herself, where the system had taken it all online.  But she wouldn't be the same Dragon he knew.  The organic A.I. architecture would develop in different ways, with different nuances.  So many things connected to so many other things with each new experience, and the connections would occur in a different fashion.



No, he realized.  Even worse.  He would have to head her off before she got access to the data.  If he had to load that backup, he would be loading her as she was before he freed her of the PRT's shackles.  She would be obligated to fight him.  He'd managed a sneak attack the first time.  The second?  She'd see what he did, force him to try another means.



And he'd have to be \emph{more} ruthless, knowing he was doing harm to her, injuring her to her core.



He couldn't bear to watch further.  It was too soon to try another backup, both in terms of the system's ability to handle the task and his own ability.  But sitting here, watching the list of errors grow, it was angering him, and it was an anger without a focus.



Touching two fingers to his lips, Colin moved those fingers to the monitor's frame, pressing them there.  The gesture was sentimental enough it felt unlike him, somehow \emph{false}.  Doing nothing would feel wrong too.



That was his current state, stranded inside his own head, in the midst of his own feelings.



Uncharted territory, in a way.



He pulled on his helmet and stepped outside, and hopped up onto the nose of the Tiamat II.



New Delhi loomed before him.  Ruined, damaged, impossible to recover.  The sun was only now setting, and the sky was red, mingling with the traces of clouds that still remained in the sky.



He wanted to contact Chevalier, to know that his friend was okay, that the \emph{Protectorate} was okay.  He didn't trust himself to stay calm, to keep from saying something about Dragon, from venting, being emotional.



Chevalier would understand, he suspected.  But Colin's masculinity would take a hit, and it would only cause more trouble than it fixed.



Staring out at the city, and the crowds of people in hazmat suits who were moving in for relief, for search and rescue, he frowned.  He and Dragon had had some intense discussions on the subject of what it was to be a `man'.  To be human, to be masculine, feminine.



Dragon had been \emph{pissed} when he'd suggested she was the feminine ideal.  That, in the eternal crisis that any woman faced between being the virgin, the madonna, and being sensual, sexual, she was \emph{both}.



He wished he understood why she'd been so angry.



To be a \emph{man}, though, it wasn't much easier.  The standard society set was just as high.  To be a provider, a rock, to be sensitive, yet to avoid being \emph{emotional}.



For long minutes, he stared out over the city, watching the sun dip beneath the horizon, the smoke and dust making the distant star's light hazier, fuzzier.



``Tiamat II,'' he said.  ``Alert me when the system is finished the backup process, one way or another.''



``\emph{Yes, Defiant}.''



Uncomfortably similar to Dragon's voice.  He felt an ache in his chest.



He hopped down from the nose of the craft, then used his spear to help himself down from the craggy edge of terrain that had been raised up from the earth in the chaos.  He strode forward, towards the city proper, calibrating his helmet to help identify any warm bodies.



\blacksquare



``Annex?  Kirk?''



Kirk sat up from the hospital bed.



``You can stay where you are,'' the doctor said, not looking up from the clipboard.



``I'm okay,'' Kirk said.



``Your test results are taking some time, I'm sorry.  We can expect a two or three-hour wait.  Half an hour for the MRI, forty-five minutes for the CT scan.''



``At least it's \emph{something} to do,'' Kirk replied.



``You'd be surprised at how quickly it gets boring,'' the doctor answered.



Kirk winced.  ``Okay.  Can I maybe use a phone in the meantime?  Call my parents?  They'll be wondering.''



``They've already been informed,'' the man answered.  ``They'll be here shortly.  There's paperwork they'll have to sign, because a few of your teammates are also walking around without any protection for their identities, but I don't imagine that'll take long.''



``Maybe I can call my friends?  They'll be wondering how I'm doing.''



``They know about your life in costume?''



``They were there when I got my powers.  I just want to call someone, \emph{anyone} I know, to occupy my thoughts, to \emph{talk}.''



``There's a phone at the nurse's station, center of the floor.  Ask and they'll punch in the number to dial out.''



``Okay,'' Kirk said, smiling.  He gripped the side of his hospital gown to bind it shut.



``I\ldots'' the doctor started, he stopped and frowned.



Kirk had halted in his tracks, shifting his weight to keep his bare feet from making too much contact with the cold floor.



Odd, in a way, that he had to.  But his power tended to be all or nothing.



``I shouldn't tell you this, and I'm not naming names, but the first test results have come in, for some of the others who were at your side in New Delhi.  Here, and in other cities.  The tests for radiation are coming back negative.''



Kirk blinked.



``No promises it'll be the same for you, but\ldots''



``A bit of hope?'' Kirk asked.



``With luck.''



``Thank you,'' Kirk said, smiling for the first time.  ``Thank you.''



``I should be the one saying that to you,'' the doctor said.  ``Just\ldots don't be too disappointed if the answer isn't what you wanted, okay?''



``Deal,'' Kirk answered.



\blacksquare



``\ldotsfurther reports are coming in from multiple sources.  The Endbringer Behemoth has been reported as being slain in New Delhi!''



``Yes, Lizbeth.  Video footage is always scarce when dealing with the Endbringers, but verification has been consistent from multiple sources.  It seems the footage seen earlier of the great shaft of light was an \emph{attack} from an unknown party, debilitating the Endbringer.  Defending forces held the injured monster off until Scion could arrive, delivering a finishing blow.''



``Earlier in the year, for those of you who don't remember, Chevalier boasted of a new Protectorate, clear of the sabotage and interference from its \emph{own leaders}.  Today may serve as a testament to that boast.''



``All around the world, people seem to be celebrating, but it's a markedly \emph{cautious} celebration.  Early polls on the UKCC web site suggest that a full \emph{eighteen} percent of people who voted are waiting for more information or verification before celebrating the heroes' victory, and \emph{ten} percent of people don't intend to celebrate \emph{at all}.''



``Not at all?''



``No, Lizbeth.  In the comments thread of the poll, a common trend seems to be the feeling that he isn't or can't be dead, that the heroes were mistaken, or that this might even provoke a response from the remaining Endbringers.''



``Amazing.  We're just now getting more information\ldots''



\blacksquare



``Dad?''



``Taylor!  Oh my god.  You're alive.''



``I wasn't sure if you wanted me-''



``Are you hurt?''



``I'm okay.  I just got the tests back, and there's no sign of ambient radiation or any of that.''



``I'm glad.''



``Me too.  I wasn't sure if you wanted me to call.  You haven't replied to my messages, about being there if and when they invite me to the Wards.  And you were there for court, but you didn't talk to me.''



``I \emph{am} glad you called.  About my not-''



``We killed him.''  The words were blurted out.



There was silence on the line.



``Behemoth is dead.''



Silence, still.



``We killed him,'' the words were a repeat of earlier.  As if that summed it up.  ``I think it's already on the news.''



``I know.  I saw, but I didn't quite believe it.  I'm dumbfounded.  Amazed.  I'm so proud of you.  Wow.''



``I wanted to tell you before you heard from others, but there's so much goddamn bureaucracy going on, and they wouldn't give me a phone in the hospital room.''



``Were you- did you help?  Were you a part of that?''



``Yes.  Of course.''



``I'm just\ldots I'm trying to wrap my head around it.  Wow.''



There was a silence on the other end, this time.



``Taylor?''



``I've had a lot of time to think, to wonder why you didn't come.  Why you haven't visited me.  You're \emph{afraid} of me.''



``Taylor, that's not-''



``It's true, isn't it?  And all of the doubts I had before dialing the phone and calling you, they were right, this makes it \emph{worse}.  I have a rap sheet that's like, eighty pages thick, and I killed a man, and then I killed Director Tagg and Alexandria.  She \emph{is} dead, by the way.  If you see her on the news, it's just a cape that stole her body.  Her corpse.  And now you hear about me fighting Behemoth and it makes it \emph{worse}.  I can't even talk about what I \emph{did} without digging the knife in deeper.''



``Taylor, no.  It's not fear.  I saw some of your friends, not long ago.  I wanted to talk to your employee, Charlotte, and the others came.  And I saw this whole other life, this side of you I couldn't recognize at all.  Little things that I recognized, yes, and then big things that I could barely fathom.  I've never been able to handle loss well, with Annette, and now feeling like I maybe lost \emph{you}\ldots  I just\ldots I want to adjust, to get my head around this, and then I can visit and things will be like they were.''



``Things aren't going to be like they were, dad.  I don't want them to be.  I'm trying to put as much distance between the person I was \emph{then} and the person I am now as I can.  I'm sucking pretty hard at it, but I'm trying.  Except maybe today, I found a middle ground.  And it worked, in a way that makes me proud and terrified and amazed and confused and apparently I'm in \emph{trouble} for something I did.  I'm in \emph{trouble} because I was wearing a camera and they saw the footage and I was walking that middle ground between the person I \emph{was} and the person they want me to be, and I did a lot of borderline sketchy shit just to get \emph{by} and they don't \emph{understand}.''



There was a note of emotion in the last word, a break in the rant.



``Taylor\ldots''



One word, and then silence.



The voice was calmer this time, more measured.  ``I'm sorry.  I'm really tired.  I'm going in soon.  To talk to them.  They've made it clear they aren't happy.  Except I think they're a little bit afraid of me too.  Afraid of me like my own \emph{dad} is.''



``That's not fair.''



``\emph{Deny it}.''



There was a pause.



``I'm not afraid, Taylor.  If there's any fear, my love for you outweighs it by far, understand?''



But the phone was already steadily buzzing with a dial tone.  The pause was enough.



\blacksquare



\blacklozenge  Topic:  Footage
In:  Boards \blacktriangleright World News \blacktriangleright Main
Bagrat (Original Poster)
Posted on July 26th, 2011:



Link \underline{\strong{here}.}



Mirrors \underline{\strong{here}}, \underline{\strong{here}} and \underline{\strong{here}}.



Came directly to me.  Cuts in and out, but that's to be expected.



More info later.  Better to watch and see for yourself than get it here.



\strong{(Showing page 39 of 39)}



\blacktriangleright  \strong{Thatdude}
Replied on July 26th, 2011:
@ Bystander
I don't know, but holy shit was that intense.  I wish there was more at the end.



\blacktriangleright  Mane MagentaReplied on July 26th, 2011:
When Scion uses his power it disturbs electronics.  Its why when he flies you can't track him unless its with your eyes.
Omg.  I'm only halfway through.  This is almost a feature length film.



\blacktriangleright  \strong{Dawgsmiles} (Veteran poster)
Replied on July 26th, 2011:
anyone else have to look up some of the people in there?  i almost thought one or two weren't villains



\blacktriangleright  \strong{Saskatchew}
Replied on July 26th, 2011:
It's kind of terrifying, isn't it?  There's only like twenty in my province but you think maybe **one** can do something like we saw partway through and its like wow holy shit I could run into them in the street at any time



\blacktriangleright  \strong{Feychick}
Replied on July 26th, 2011:
holy fuck holy fuck holy fuck
(56 minutes in).



\blacktriangleright  \strong{Ne}
Replied on July 26th, 2011:
@49:00 When she's talking to the guy in blue.  Who is that?  Not in the wiki.  How do you even SPELL that?  She turns on her friend?  What happens to that guy?  Did he die?  Did she get him killed?



\blacktriangleright  Forgotten CreatorReplied on July 26th, 2011:
@ Dawgsmiles – I had to look up one or two.  There was a short doc about some of them a bit ago after Alexandria died.  You can find it \underline{\strong{here.}}



\blacktriangleright \strong{Logs}Replied on July 26th, 2011:
Let's see:



%%% <blockquote>
<ul>
<li>Note the link back to <span style=""><strong>this thread</strong></span> just earlier today.  (Kid has Weaver show up for Wards event at park.)  Paraphrasing hearsay: ‘I had everything, I gave it up’.  You can see how much she cares about them.</li>
<li>Is the Echidna thing tied to the mysterious info-blackout in Brockton Bay re: time portal created?</li>
<li>Wondering about Tecton.  Liking his talk about powers and building teams, but he defects leadership to known ex-villain who knows little to nothing about his team?</li>
<li>Anyone else wondering why they went with the ‘V’ hand sign?  That’s a rude gesture in New Delhi<em>, </em>99% sure.  Americans.</li>
<li>Intimate moment b/w Weaver and Grue.  Anyone else feel like a pervert watching this?  Can’t see anything, but I think they’re kissing.  If I thought this was staged I stopped when this happened.</li>
<li>Regent/girl with gray mask (forget name) funny as hell.  Hoping they all make it out okay.</li>
<li>Have to stop at 12 minute mark.  Burned girl.  Too real.</li>
</ul>
</blockquote>



\blacktriangleright \strong{General Prancer}
Replied on July 26th, 2011:
anyone else \emph{really} interested in learning more about Weaver?
edit:  @Logs: don't get too attached to anyone.



%%% <p style="text-align:left;padding-left:30px;">► <strong>Noveltry</strong><br/>
Replied on July 26th, 2011:<strong></strong><strong style="padding-left:30px;"></strong><br/>
This cuts out at the <span style="text-decoration:underline;">most</span> frustrating times.</p>



End of Page.   \underline{1}, \underline{2}, \underline{3}, \underline{4}, \underline{5} \ldots \underline{38}, 39



\blacksquare



Glenn reached across his keyboard to refresh his email, then hit the key on his keyboard to shut down the machine.  While the screen went through the motions, Glenn walked around the desk to kneel on the floor.  The computer itself was set into a recess in the floor, and he worked at unplugging and unscrewing each wire in turn.



A butterfly flew across his field of vision, and he jumped despite himself.



``Weaver,'' he said, turning around.



``Glenn,'' she said.  She wasn't in costume, but her glower was intense enough that she might as well have been in her full garb as Skitter, complete with shawl, skirt and the carpet of insects crawling on her.



``Recuperating?''



``Not as much as I'd like,'' she said.  Her voice was hard.  ``I'm not having the best day, on a lot of levels.''



``Still waiting for the tribunal to convene?''  Glenn asked.  ``It's been hours now.''



``The secretary's supposed to call me.  They gave me one of the superhero phones so I could call my dad, told me to hold onto it.  I'd take it as a good sign, except there's a video circulating online.  \emph{My} video.  Well past the point where anyone could hope to control access to it.  Mirrors, bitsharing, hardcopies\ldots''



``I see.  Upsetting.''



``Yeah.  Just a little,'' she said.  The tone was light, but her expression remained the same.  ``Packing up?''



``Yes,'' Glenn said.  He tried to lift the desktop, found more wires attached at the bottom, and set it down to unplug them.



``I expect I'll be fired.  They'll make me clean out my office, so I figured I would get a headstart.  I don't keep anything permanent that isn't on my personal computer, so this box is all I need.''



She didn't respond.



He tried to lift it again, only to find more wires connected on the \emph{front}.



``No need to worry.  If you're here to inflict some bug-induced torture on me, you can save yourself a lot of effort by leaving me to my own devices with this damned \emph{box}.  I promise you, I'll figure out something worse to do to myself.''



Butterflies circled her as she stalked forward.  Glenn backed away a step before he realized what she was doing.  She wasn't even a third of his weight, and the only insects she seemed to have on hand were butterflies, but he felt a touch intimidated nonetheless.



Were the butterflies supposed to be ironic?  A gesture?



She knelt down beside the computer, fiddled around and disconnected the remaining wires, then lifted the box up to the floor beside the recess.



``Thank you.  I'm good with computers, with software, but laughably bad with the \emph{technology}.''



``\emph{Why}, Glenn?  It was private.  It was supposed to be for therapy.''



``Wasn't my choice to parcel it out.  Dragon was killed, by all accounts, and Director Wilkins made the call to hand it out, for your pending conduct review.''



``And you made the call to release it online.''



``I suppose Tattletale informed you.  Do you know how frustrating it is to be a mere human being among powers like you and your friend?''



``I dunno,'' she said.  ``I figure you can relieve your stress by uploading their personal videos to the internet.''



Glenn sighed.  ``You're tired.  You're not being rational.''



``Oh, yeah.  That's totally the way to talk to a girl.''



Glenn stepped forwards, resisted the urge to flinch as the butterflies briefly invaded his personal space.  He met her eyes, waited for her to look away, then snapped, right in front of her.



Her eyes locked onto his, and she looked even more irritated.



``Stop,'' he said.  ``Look me in the eyes.  I want to talk to Weaver the strategist, not \emph{Taylor}.''



She didn't move a muscle, but he wondered if the butterflies changed course.  She remained silent, glowering.



``I know you're tired.  Today took a lot out of you,'' Glenn said.  ``But \emph{think}.  What purpose does it serve to upload the video?''



``It's the best footage you have of the event.  The best way to sell the win, the PRT's involvement.''



``Think bigger.''



``That's pretty damn big.''



``\emph{Bigger}, Weaver.  Come on.  Do you think I got to where I am by thinking one dimensionally?  What else, why?  I'm getting \emph{fired}.  I \emph{knew} I'd get fired.  Would I do it just for that?''



``Probably, if there wasn't another way.''



``With an ego like mine?''



``Honestly, your ego can't be that big if you wear those clothes.''



Despite himself, he was a little stung.  He'd cultivated his image to \emph{demand} attention.  Even his weight was calculated, to make it clear he was not one of \emph{them}, that he was someone with power, presence.  His clothes were admittedly awful.  They were \emph{intended} to be awful.  But they didn't diminish his sense of pride in the least.



It was a shame he was undoubtedly going to lose his job.  It would be nice to discuss the idea of image from two very different perspectives.



``I'm not your adversary, Weaver.''



``No.  I can't help but feel you're an albatross around my neck.  I keep hearing that you've done stuff to help, but I keep \emph{experiencing} this\ldots \emph{this}.''



``I'm your \emph{ally}, Weaver.  You think I don't recognize the issues in the PRT?  The corruption that's still at the core?  The need for \emph{change}?  There has to be some sacrifice, and there has to be someone to step forward, a \emph{harbinger} for that change.  Chevalier may be the hero of the day, he can lay the groundwork for change, but he can't be that harbinger.  He's too entrenched.''



``You want me to be the harbinger.''



``It'll be hard, but I think you'll manage with that.  Putting this video online, it's going to achieve a lot of things.  I think, seeing you in the thick of it, it's going to change people's opinion of you.  There'll be controversy, some will hate you.  But others?  This will be their first view of what it's truly like on the battlefield.  They'll \emph{have} to like you, to sympathize.  But the rule of three says you won't be forgotten about.''



``Rule of three?''



``Three times, you've been forced into the public eye.  As the leader of Brockton Bay, as the newly christened Weaver, slayer of Alexandria, and here, in the video.''



``I was just thinking about something like that, in a totally different way.  Twice now, I've betrayed my teammates.  At first, when they found out I was an aspiring hero, an undercover operative.  Then I became Weaver.  This'll be the third.  I had the camera, stuff was said and done, private stuff talked about, and they won't like it.  They didn't ask to be in the spotlight any more than I did.''



``Some of it will endear you to the public,'' Glenn said.



``Being worshipped as a \emph{god} wouldn't be worth hurting them again,'' Weaver retorted.  Her voice was hard again.  ``Grue believes that image and reputation are a kind of protection.  Being seen as \emph{soft}, when he's dealing with people in the criminal underworld?  It could get him \emph{killed}.''



``They'll forgive you that setback, I'm sure.  They'll understand you didn't choose to do it.''



``Rachel's not the \emph{understanding} type.  I've fought an uphill battle to get her trust, and if she feels hurt by this, or if she registers that others are hurt, and that I'm the culprit in any way-''



``With luck, public opinion and an insight into the bond you have with the team will make it \emph{easier} to interact with your old team.  You'll have more chances to fix any damage.''



Weaver shook her head, staring down at the ground.



``It's an honest look into what the heroes do, Weaver.  What you capes face every day.  Why there's so much gray in the moral palette.  With this, Chevalier's new Protectorate won't be something that exists in name only.''



``You could have \emph{asked}.''



``You would have said no.  And there was no time.  We needed to make it absolutely clear just what you and the rest of the heroes did on the field, so Scion couldn't overshadow you.  We needed to do it right away.  Cement the idea into the public mind so it was the first \emph{concrete} piece of information they got.''



She stared at the ground.  The lines in her face were deep with exhaustion.  The butterflies had landed on her shoulders and arms.



He let the idea sit.  Better to let her speak next.



She did.  ``Chevalier is laying the groundwork, I'm the harbinger\ldots and you're the sacrifice, then?''



He met her eyes.  ``They won't be as upset with you as they are right this moment.  I'll draw the initial heat.  By the time they're done with me, my career and any possible job in a related field will be ashes in the wind.  For you, well, it'll tip the scales.  If you're halfway into the `deserves a medal' camp and halfway into the `needs to be punished' camp, this will help.''



``I could have done some things better, but was I that bad?''



``Consorting with villains you were supposed to avoid, putting Wards on the line to help them, dealing with Phir S\textoverline{e} without contacting any superiors.  You ignored the rules regarding image, took gambles-''



``I \emph{had} to.  All of that.  I was told that rules are relaxed on the field.  You can't seriously expect me to use \emph{butterflies} against Behemoth.''



``Of course not,'' Glenn responded.  ``Do you think I'm stupid?  I \emph{know} this.  But there's a lot of people paying attention to this.  Many people who will be in that room won't know these things, won't fully understand.  Some won't even watch the video before they pass judgement on what occurred in it.  \emph{Never} underestimate the stupidity of people.''



Weaver made a sound, halfway to a sigh, halfway to a laugh.



Glenn smiled a little.  ``The video burns one bridge.  No more butterflies.  Though they won't hurt, because it makes it a hell of a lot harder for any common criminals to complain about an excess use of power, but I'm digressing\ldots''



Weaver's phone beeped.  A moment later, Glenn's vibrated.  He checked it.



Convening to discuss Weaver's conduct in room F.  Please attend.



He closed the message window.



``Thank you,'' Weaver said.  ``I think.  I'm supposed to go now.''



``Me too.  Join me?''  Glenn asked.



Weaver nodded.  Her collection of butterflies led the way out of the office.



Glenn spoke without looking at her.  ``I don't expect you to like me.  Never really did.  One of the first and biggest problems you ran into was with your image.  It's a problem even now, I suspect.  It will continue to be a problem, especially now that you're in the limelight.''



``Uh huh.''



Glenn reached into his vest pocket and withdrew a case.  He opened it, removed a business card, and handed it over.



``My number.  In case you need advice.  Well, use my cell.  My work number probably won't be mine for much longer.''



Weaver stared down at the card.  She didn't need to look up as she walked, as the butterflies checked her path for her.  Other bugs had joined them.



``Just do me a favor,'' Glenn said.



Weaver glanced at him.



``Make friends with whoever they hire to replace me.  Listen to them.  You're allowed to hate them too, but hear them out.  Can't hurt.''



She nodded.  She looked down at the card again, then looked up at him.  ``Can I call this in now?  It's about my dad.''



\blacksquare



``\emph{Defiant?}''



Defiant couldn't move, as he held a heavy concrete slab out of the way for emergency crews.  He used the cursor embedded in his eye to select the `answer' command, and shut the vents around his mouth.



``Tiamat II, hold off on any reports for now.'' \emph{Can't take it, not right this moment}.



``\emph{It's me.}''





