





The news came through the earbuds, and it was like a shockwave rippled through our assembled ranks.  Some of the strongest of us dropped to their knees, staggered, or planted their feet further apart as though they were bracing against a physical impact.



The one Azazel that was still in the area landed atop one of Bohu's buildings, nearly falling as a section slid off to drop to the empty street below.  It found its footing and roosted there.



The pilot couldn't fly, and the A.I. wasn't willing or able to take over.



The other capes were talking, shouting, asking questions, sometimes to nobody in particular.  With the blood churning in my ears, I couldn't make out the words.  I'd used my bugs to find Hookwolf's core, but they'd been decimated twice over in the process, and I wasn't interested in trying to use them to figure out what was being said.



I could guess.



I raised my arms, then found myself unsure what to do with them.  Hug them against my body?  Hit something?  Reach out to someone?



I let my hands drop to my sides.



I opened my mouth to speak, to shout, to cry out, swear at the overcast sky above us.



Then I shut it.



There were no words.  Anything I could do or say felt insignificant in the grand scheme of it all.  I could have used every bug in the city to utter something, something meaningful or crude, and it still would have felt petty.



I looked at the others.  Clockblocker was with Kid Win and Vista, Crucible and Toggle were nearby, on the back of a PRT van, bandaged.  They were looking over their shoulders at the screen mounted on the wall of the van.  Footage, covering ruined landscapes, and what had used to be the United Kingdom.



Parian and Foil were hugging.  Odd, to see Foil hunched over, leaning on Parian for support, her forehead resting at the corner of Parian's neck and shoulder.  The crossbow had fallen to the ground, forgotten.



I wanted something like that.  To have a team close, to hold someone.  I hadn't had something like that in a good while.



Chevalier was a distance away, his cannonblade plunged into the ground so he didn't need to hold it, a phone to his ear.  He was talking, giving orders, and demanding information.



Revel was stock still, not far from him.  I watched as she stepped back, leaning against a wall, then let herself slide down until she was sitting on the street.  She placed her head in her hands.



I'd never known her to show any weakness.  She'd always been on the ball, always the leader.  I knew how much concussions sucked, and I'd seen her carry on and contribute to the Behemoth fight when she was reeling from one.



It hit me harder than I might have expected, to see that.



Tecton was standing a distance away, almost frozen, his eyes on the screen of his armband.  Golem did the same, but he wasn't still.  He paced, looking around for guidance and finding none, then turned back to the screen, watching.



Glancing at the images from a distance, I could see the figure, the speck visible on the long range camera, surrounded by a golden nimbus.



I wasn't close enough to make out details.  Only staccato flares of golden-white light.  On the third, the screens fizzled, showing only brief gray static, then darkness.



Another target hit.  He'd taken his time on that one, measured the attacks.



I took out my earbud before the report could come in.  Not my focus right now.



Instead, I reached for my phone.  I dialed the Dragonfly.



Would the A.I. be able to cope?  Saint had apparently pulled something.



If there was \emph{any} hint he fucked us here, he'd pay for it.



The phone responded with a message.  An ETA.



My eyes turned to Rachel.  She was more agitated than Golem, her attention on her dogs.  She used a knife to cut away the excess flesh and retrieve the animals from the placenta-like sacs within their bodies, and the actions were aggressive, vicious, savage.  Her expression was neutral, but I could see the way the muscles shifted in her back, beneath the sleeveless t-shirt she wore, the tension, the way she was hunched over.



The attitude fit the Bitch I'd been introduced to, way back when I'd first joined the Undersiders, not the Rachel I'd come to know, who'd found a kind of peace.



Angry, defensive, bewildered.  Scared of a world she didn't comprehend.  Aggressiveness was the default, the go-to route when there weren't any answers.



It dawned on me.  I \emph{sympathized}.  Given a chance, given something to do in that same vein, hacking through dead meat with a knife for some defined purpose, I might have acted exactly the same way.



She flinched as I approached, as if I were invading her personal space.  When she turned and glanced at me out of the corner of one eye, glowering, the tension faded.



I drew my own knife and started helping.  Bugs flowed into the gap and gave me a sense of where the sac was.  I was able to cut without risking cutting the dog inside.  It helped that my knife was sharp.



We were both sweating by the time we finished.  Rachel had already been sweating from more physical exertion, and her hair was stuck to her shoulders at the ends.  The German Shepherd got free, walked a polite distance away and then shook herself dry.



I looked at my phone, my gray gloves crimson with the dog's blood.  There were incoming messages.  Updates on the damage, the disaster, and on Scion's current location.



I ignored them, looking for the Dragonfly's status.



Minutes away.  It had already been headed into the area by default, tracking me by my GPS, ready to maintain a constant distance until I was prepared to call for it.



That was fine.  I started walking down the length of the street, my back to the others, to the Azazels and the heroes.  Rachel fell into step just a bit behind me, her dogs and Bastard accompanying us.



Parian and Foil were still hugging.  I paused as we passed them, tried to think of how to word the invitation.



Parian's eyes weren't visible, hidden behind the lenses on the white porcelain mask she wore.  I hadn't thought she was looking at me, but she shook her head a little.



Good.  Easier.  I left them behind.



The Dragonfly started to land in an open area, an intersection of two streets.  Moments later, the ground began to crumble.  The craft shifted position, coming perilously close to striking a building as it avoided falling into the hole that had appeared in the street.  A trap.



Rachel boarded the craft.  As I waited for the dogs and Bastard to join us, I looked into the pit.  As deep as a six or seven story building was tall.



I turned away, boarding the Dragonfly.  I plotted a course, then took manual control of the craft.



The A.I. was better at flying than I was, but flying meant I didn't have to think.  Didn't have to worry about what I was about to find out.



Rachel didn't seat herself at the bench along the wall, or even at the chair behind mine.  She sat down beside me, on the floor of the Dragonfly, her back against the side of my seat, the side of my leg, staring out the narrow side window.  It was physical contact, reassurance, seeking that same reassurance from me.  Her dogs settled on either side of her, Bastard resting his head on her lap.



We had the whole country to cross.  Every few minutes brought more visuals, more reminders of what had occurred.  Highways grew choked with cars.  Countless vehicles had stopped at the sides of roads, at the edges of fields and at the fringes of small towns.



Innumerable people running, seeking escape.  Except there wasn't anyplace good to escape \emph{to}.



No.  That wasn't true.  There \emph{was}.



But the degree of the damage done was becoming clear.  Before we even reached the East coast, I could see the damage done to the landscape.  Smoke was only just settling around the cracks and fissures, fallen bridges and ruined highways.  People were making concerted attempts to move, to \emph{leave}, but every step of the way brought more difficulties, more forced detours.  Some had abandoned cars altogether, wading or swimming across rivers to make their way.



Every step of the trip revealed more devastation, successively more vehicles choking roads and highways, forging paths around impassable roads.  More and more people were forging ahead on foot, in crowds, because walking was faster than travel by car.



More helicopters, marked with red crosses, had taken to the skies.  Travel by ambulance wasn't doable.



This was \emph{one} place.  One moment's attack.  The display in the cockpit was showing more locations hit.  Libya, Russia, France, Sweden, Iran, Russia again, China\ldots



Time passed.  Forty-five minutes from the point in time I started paying attention to the clock, searching for a yardstick to try to track the scale of what I was seeing on the surface.  How much worse did things get in five more minutes of traveling?  In ten?  It all seemed to get exponentially worse as the Dragonfly took flight.  It wasn't just that we were getting closer to the point where the attack had hit.  Enough time had passed that people could \emph{react}, now, realizing just how severe this was.  All of the power of Behemoth, mobility almost on par with Khonsu.



The psychological toll of a Simurgh attack.



\emph{These} were the people with a strategy.  Doing just what I'd be doing if I were one of the unpowered.  The world was doomed, so they sought to flee to another world.  Problem was, there were tens of millions of them, and the escape routes were scarce at best.



The best known escape route: Brockton Bay.



I felt my heart sink as we approached the coast.  Mountains I'd grown up with weren't there.  I let the autopilot take over as we got closer, approaching an airspace choked by rescue aircraft.



I didn't trust my own hands.



It had collapsed.  The blast had only struck the northern edge of Brockton Bay, then changed orientation, striking through the bay itself to slice through the very foundation the city sat on.  Everything had been dropped a solid thirty or forty feet.  Tall buildings had collapsed and only the squatter, sturdier structures and those fortunate enough to come to rest against other buildings were still mostly erect.



Folding and collapsing, the entire city had been shattered, no section of the ground more than twenty-five feet across remained fully intact.  The landscape rose and fell like waves, petrified and left frozen in time.



The portal tower had fallen, but the portal remained there, oddly bright, too high to reach on foot.  Work crews were struggling to erect something beneath, so the civilians could finish their journeys.  The new arrivals were alternately joining in with the construction and making their way inside by way of rope ladders.



Elsewhere, there were capes and rescue crews trying to contain the fallout around the scar.  A structure had been raised to seal it off, but the collapse of the city had released the contents.  A lot of containment foam was being deployed to slow the spread of a pale patch of earth, and there was one spot of fire that didn't seem to be going out.



But the most eye-catching thing was a thin, scintillating forcefield that was holding off the water.  It was taller than any building that had stood in the city, an artificial dam.  Every few minutes, it flickered for a tenth of a second, and water would flood through to seep into the gaps and fissures.  In time, I suspected, the water would cover everything in the area but the tallest buildings and the hills.  Arcadia High might stick around.  Maybe.



I recognized the rainbow hues.  It was the same force field that had been intended to protect the Protectorate headquarters.  Leviathan had torn the structure apart at the roots, and the tidal wave had knocked it into the city proper.  In the time since I'd left, they'd repurposed the fallen structure and the forcefield setup.



Not, apparently, to try to block Scion's attack.  No.  This was more to stop the water, to break that initial wave, so it wouldn't simply sweep the ruins out to sea.



I could only hope they'd done similar things elsewhere, to minimize the damage.



We circled the city twice before I gave the go-ahead for the A.I. to start descending.



My second sense extended through the area as we approached the ground, extending out to the bugs that were scattered throughout the ruined, shattered city.  I immediately set them to work, searching, scanning, investigating.



I changed the course, dictating a final, slow, sweep of the city.



Not everyone had made it.  Stupid to think they might.



My dad's house was gone, collapsed.  Nobody inside.



Winslow High, gone.



The mall, the library, Fugly Bob's, the boat graveyard, my old hideout, gone.



My old territory, unrecognizable.  The Boardwalk was underwater now.



It didn't even take him \emph{seconds} to do.



Too many dead, not enough who were merely wounded and unable to walk.  Humans were so fragile in the end.  I stopped the Dragonfly and stepped out to seek out the first wounded.  My bugs signaled rescue teams to get their attention.



The wounded here could have been my dad's coworkers.  People he went out to drinks with.  They could have been Charlotte's underlings.



So easy, in the midst of it all, to lose track of the fact that these were \emph{people}.  People with families, friends, with dreams, lives and goals.



Golem had said something like that, hadn't he?



How many people had simply been \emph{erased} in the wake of something this random, so instantaneous?  So inexplicable?  I still wasn't sure what had happened.  Tattletale was supposed to fill people in, but she hadn't gotten in contact with me.



Or had she?  I'd taken my earbud out.  I looked to my phone, looked for transmissions.



A burst of messages, following just after takeoff.  From the Chicago Protectorate, people who might have been my teammates if I'd ever been inaugurated.  More messages, from Chevalier and the Brockton Bay teams.



I didn't read them all.  My eyes on the phone, I pointed the search and rescue to the next batch of wounded.  I knew it was cold, but the corpses would have to wait.  There were living people to find.



There were no shortage of corpses.  The number of living people, by contrast, well\ldots we'd see what happened in the next twenty-four hours.



The number of messages declined about thirty minutes after takeoff, then stopped altogether.  Everyone who might have wanted to talk to me had found other things that needed doing.  Other priorities, personal or professional.



Which was exactly why I was here.  I'd just arrived at that conclusion earlier than they had.  I put my phone away.



My mouth was pressed into a firm line as I helped the rescue workers.



We lifted a corner of a second floor's floor, making room for someone get under and start retrieving a pair of women.  Rachel whistled and pointed, and her German Shepherd seized the floor in its jaws.



The rescue workers seemed to hesitate with the dog's presence, so I took the lead, crawling inside on my stomach.  I used my hands with the arms on my flight pack to move enough debris that we could slide the second woman out.



There were more.  Almost without thinking about it, I let myself slide back into the mindset I'd held for the past two years.  Sublimating what I wanted to do in favor of doing what \emph{needed} to be done.



Minutes ran into one another as we worked.  I could see Rachel growing progressively more short-tempered, slower to give the orders, hanging back, rushing with the jobs.



That ended when we rescued a child that had a puppy wrapped in her arms.  She clutched the limp animal like it was a security blanket, not crying, not speaking.  She only stared at the ground, coughing hoarsely whenever she had to move.  Her parents had been on either side of her, and neither had made it.



The paramedics fit her with an oxygen mask, but they failed to pry the animal from her arms.



I looked at Rachel, but she only shook her head.



Rachel's power healed animals, but this one was gone.



From the moment we left that girl to be loaded onto a stretcher and carried off to firmer ground, Rachel moved a little more quickly, a little more decisively.



We finished with one site where the ground had collapsed and people had fallen into a depression, and then moved on to the next area.  Some heroes were working alongside the authorities to try to rescue people from a building that had partially tipped over.



Clockblocker was there, along with Vista.  I joined my powers to theirs in finding people and opening the way.  Frozen time was used on panels, which were subsequently layered, so that one could offer support if another stopped working prematurely.  Vista reinforced areas, then opened doorways, as I designated rooms where people were trapped within.



A golden light streaked across the sky in the wake of Scion's flight, just along the horizon.  A thinner beam being directed from Scion to the ground as he passed.



The aftershock of his passing took time to reach us.  Steam started to billow, but the forcefield absorbed it.



The shuddering of the ground was more problematic.  The entire city rumbled in response to the distant attack, a blow that was no doubt slicing deep into the earth's crust, forcing \emph{everything} to resettle.



The building we were working on was among those things that resettled.  I watched as the building started to slide where it was resting against the building beside it, slowly descending, building speed.



My flight pack kicked in, and I flew through a window.  I could feel the glass scrape against my scalp and the fabric of my costume.



I found one person, a twenty-something guy, took hold of their wrist, and pulled them behind me, running and using my flight pack at the same time.



Tearing him through the window meant slashing him against the shattered glass, and the weight wasn't something I could manage with my flight pack.  The building fell down around the people on the ground as I fell too far, too fast.



The wing on my flight pack was still broken.  Couldn't trust the propulsion.



I let him fall into a tree instead, from a solid two stories above, and then focused the rest of my energy into pulling out of the plunge.



The building was still crumbling as I landed a distance away.  The rumble brought other, smaller structures down.  I stood and watched as it continued its course.



There'd been seven more people to rescue inside.  The other buildings in the area that had been caught up in the domino effect had contained three more.  That was just in my range.  How many more were dying as he continued towards the mainland, cutting deep into the plate of land that the landmass was perched on?



He hadn't even been \emph{near} us.  Closer to New York or Philadelphia than anything.  More lives taken, purely collateral.



When the dust settled, I moved in to help the people who had been on the ground.  Vista and Clockblocker had protected most, between a dome and a shelf of land to provide shelter.  Rachel, for her part, had helped others run in time, snatching them up with her dogs, but I counted three more dead, one dying.



Seeing them like that, bleeding, still warm, it caught me off guard.  A kind of anxiety rose in the pit of my stomach, like an impulse to \emph{do} something coupled with the frustration of knowing that everything I could manage to come up with was futile, hopeless.  I either couldn't do anything or I couldn't think of what to do.  It put me in mind of being back at high school, before I had my powers.  Of being a child, powerless and unable to act.



I saw the image of Parian holding Foil in my mind's eye, and it was joined by an almost sick feeling of mingled relief and fear.  I knew exactly what I wanted and I was terrified to seek it out.



I could feel that same impatience Rachel had expressed earlier, but I couldn't turn my back on this.  I got the guy out of the tree and found him okay, but for a broken arm.  He didn't thank me, but I let myself chalk that up to him being in shock.  I almost stumbled over to the latest injured and I attended to the wounded until the medics pulled themselves together, got organized and relieved me.



Then I backed away, flexing my hands, feeling how stiff they were, battered by my attempts at moving things, at pushing things aside.  My gloves, too, were stiff, crusted with dried blood, layered with dirt and \emph{fresh} blood.



I looked at Rachel, and saw her gazing at the portal.



I didn't really have a home anymore.  Knowing my old house was leveled, that the cemetery where my mother had been laid to rest was gone, and that I'd never really come back here to hang out with the Undersiders\ldots it hurt in a way that was very different from a knife wound, being shot or being burned.  A \emph{crushing} feeling, more like.  But it was tough for reasons beyond the fact that I considered it home.  I'd relinquished Brockton Bay, and my concern right now was more to do with the residents than the place itself.



I didn't have a home in Chicago.  Not in the jails, either.



But Rachel had forged a home for herself, and it had been in arm's reach since we'd arrived.



Bastard and the dogs seemed to know I'd decided before I said or did anything.  Rachel and I fell in step behind them.



Rachel mounted Bastard before we got to the portal.  The efforts to erect a proper support beneath the portal had been set back by Scion's strafing run, which left the portal hanging in the sky.  Train tracks extended out from the portal in every direction, twisted and broken where collapsing ground had pulled other sections away.



There had been a tower erected around the portal, but it had collapsed into shambles as the ground dropped.  Now they were using the pieces to form the general structure for a tower of ramps that would lead up to the portal.



Bastard picked up speed as he approached the tower, then set his claws on one of the ramps.  The tower wavered perilously as Bastard leaped up to a higher point, coming to a rest on the very top of the dilapidated structure.  It didn't look like there were \emph{nearly} enough reinforcements, and I could see everyone present tense as they saw the mutated wolf's weight come to rest.



That tension redoubled as the wolf flexed its muscles, hunching down, and then leaped, more up than across, to get to the portal itself.  A few planks of wood broke in that sudden, powerful movement, and one rail of the train track fell free as the wolf scrabbled for a grip on the ground beneath the portal.



When she was gone, the people beneath simply resumed work, heads down, dirty, defeated.



I took flight, entering the portal for the first time.



Earth Gimel.



The tower that contained the portal had a counterpart in Gimel, a matching tower, tall and riddled with train tracks, like a train station designed by Escher, tall rather than squat, with wide doorways for the trains to exit, and complicated reinforcements for the aboveground tracks, positioned so as not to interfere with the tracks below.



I flew out through one of those gates, catching up with Rachel.



Trains extended in every direction from the portal, on tracks that extended out into the middle of nowhere, into pristine forest and mountains.  They were long, almost absurdly long.



Then again, the whole idea had been to have \emph{instant} evacuation.  Rather than have people make their way to trains, they'd had eight trains that simply spanned the length of Brockton Bay, so any given individual had to find the nearest train car and make their way down the aisle to an empty seat.



Around the tower, a small, odd settlement had sprung up.  All of the sensibility of the city, but contained to a small area.  Tall buildings, wide streets, and a \emph{look} that matched up with a city proper rather than a smaller town.  It was as though someone had cut and pasted the big city into the middle of this landscape.



On any other day, it would have been energizing, the fresh air, the sunny day, the green and the blue water of the bay, subtly different from the shape of the bay I knew.  But today wasn't that day.



People at benches were clipping the corners off of refugee's drivers licenses and trading them for food rations and tents.  Everything was prepped, set up in advance, and people were being orderly, even though the lines were so lengthy it looked like it might be hours before they got what they wanted.



Those that already had their kits were setting up or settling into spaces they'd designated for themselves.  Some clustered close to the settlement, while others spaced out, where they'd have more elbow room.  The tents were identical, dotting the area.  The kits, apparently, included signs, and these same signs listed family names and details.



\emph{John and Jane Roe.  1 Diabetic.}



\emph{Hurles family.  }\emph{Two infants.}



\emph{Jason Ao.  Looking for Sharon Ao my wife.  }A crude picture was drawn beside the message.



I scanned the signs, looking for names I might recognize.  I headed in the direction Rachel had gone, but I moved carefully, making a mental note of everything I saw.



It was an extension of what I'd seen back in Los Angeles.  People trying to cope against something where coping was a pipe dream.  There were some breaking down in tears, people getting angry, those who had withdrawn into themselves.



In each expression, there was something that echoed my own feelings.  A part of me wanted to hide from that, but another part of me knew I couldn't.



It wouldn't do any good, but I made a mental note of faces, of the pain, the loss.  People who'd been removed from their homes and had all hopes for the future dashed.  If I ever had the opportunity to get revenge, to get back at Scion for doing this, I wanted to remember these faces, find just a \emph{little} more strength, make it hurt that much more.



But I wasn't one for simply \emph{wanting} to help, paying lip service and promising vengeance felt hollow.  Instead, as a token gesture, something that might not even be noticed, I gathered up every mosquito in range and proceeded to murder them with other bugs.  I kept the biting flies.



I wrapped the bugs around me.  Fuck PR.  The faint weight of the insects was reassuring, like a blanket.  A barrier against the world, like Tecton's armor or Rachel's intimidating nature.



A sign caught my eye.  I stopped, looking over the people in the small campsite.



Barnes.



No further details, no requests.  I almost hadn't recognized them.



Alan, Emma's dad, had lost weight since I'd seen him last.  He'd noticed me, and looked up, staring, his eyes red.  His wife sat in a lawn chair beside him, while Emma's older sister sat on a blanket at her mother's feet, her mother resting one hand on her head.



Zoe's -Emma's mom's- eyes were wet.  Emma's sister looked equally upset.



Emma wasn't in sight.  I could guess what they were crying about.



Alan was staring at me now, and there was an inexplicable \emph{accusation }in the look.  His wife took his hand and held it, but he didn't move his eyes a fraction.



When Anne, Emma's sister, looked up at me, there was a glimmer of the same.  A hint of \emph{blame}.



Emma hadn't made it.  How?  Why?  Why could they all leave while Emma wouldn't be able to?  I might have thought Emma had been somewhere out of reach, but that didn't fit.  There would be no certainty she was dead.  They'd be putting her name on a sign and hoping she turned up?



And why would they blame \emph{me}?  For failing to stop this from happening?



Fuck that.



I turned and walked away.



Once I was out of their immediate vicinity, I took a few running steps and let my flight pack lift me up.  Better than zig-zagging between the campsites.



I floated over a sea of people with their heads down, their expressions alternately emotional and rigidly stoic in defeat.  Hundreds or thousands of tents surrounded the area, and string fences no higher than one's calf bounded off each of the sites.



Rachel had made her way outside the city limits, past even the tents that were set a five or six minute walk from any of the others.  I followed her over the hill, to another small set of buildings.  Cabins set on what had been Captain's Hill in Earth Bet.  I knew they were Rachel's because of the dogs that were scattered around the premises, a small crowd milling around Bastard and the other mutant canines.



The largest cabin had three large bison skulls placed over the cabin door.  Bastard and the other dogs had been tied up outside like horses, left to shrink, with a trough of water to drink from.



I landed, and I was struck by the realization that my flight pack might not be so easy to recharge, now.  I still had the spare, fully charged, but Defiant might have his hands full, and the infrastructure or resources might not be available.



It was a minor thing.  Inconsequential, in terms of everything that was going on.  It wasn't like the flight pack was going to matter a bit against \emph{Scion}.  But it was one more reminder of what was truly happening.



I stopped and turned to look over the landscape.  I turned my head right until the small settlement and the sea of tents wasn't quite visible, then turned it to the left to do the same.  Focusing on the nature, the untouched wilderness.



\emph{Is this what Brockton Bay will look like, if we can't win this fight?  How many years does it take for the last building to collapse, for dirt and grass to drown away any and all signs we were ever there?}



It was a daunting thought, a heavy thought that joined countless others.



The dogs barked as I approached on foot.  I kept calm and waited.



I recognized the girl with the funny colored eyes and darker skin from Rachel's hideout.  I'd met her on my last week in Brockton Bay.  With her presence alone, the animals collectively quieted.  A single dog barked one last time, with two others reflexively following with barks of their own, but that ended it.  The girl held the door open from me, and the dogs didn't protest as I made my way inside.



Rachel was sitting on a couch with dogs arranged around her.  Angelica was afforded a bit of favoritism, and received a touch of extra attention from her master.  She, in turn, was extending a gentleness to Rachel that went beyond Angelica's poor health and the glacial movements that accompanied chronic pain.  Rachel looked defensive, her eyes cast down at the ground.  Something more severe than the whole Scion business.



Charlotte, Forrest, and Sierra were present too, keeping their distance, keeping silent as we met again for the first time in over a year and a half, not moving from where they stood.



The kids gathered at the far end of the room, silently occupying themselves with a mass of puppies.  I recognized Mason and Kathy, and \emph{didn't} recognize Ephraim at first glance.  Jessie was conspicuously absent, but nobody seemed to be reacting to that gap.  She'd left on her own, maybe.  Found family.



Aidan sat off on his own, a pigeon sitting on his knee.  He opened and closed his hands, and the bird hopped from the one knee to the other, then back again.\emph{  }Something had happened there, but it wasn't a focus.  Not right now.



Tattletale sat in her computer chair, but the computer screens were dark, the computers themselves unlit, quiet and still.



I didn't like the emotion I saw on her face any more than I liked what I saw with the others.



Pity.  Sympathy.



It wouldn't be Grue.  No.  That didn't fit.  He'd been flying back, and he hadn't been so far away that he'd be in the path of danger.



Not Imp either.  Parian and Foil had been fine the last time I'd seen.



No.



Tattletale was best situated to focus on Brockton Bay.  Who had made it.  Who hadn't.  And there was only one Brockton Bay resident who truly mattered, that hadn't been accounted for.



I felt a lump in my throat growing with every heartbeat, expanding every time I tried to swallow and failed.



Without waiting for a response, for any words of pity, or even verification, I turned and pushed my way out the door, taking flight.



I flew.  Up over the bay, away from the city, away from this alien Earth.  I blinded myself with my own swarm, drowned everything out with their drone, their buzz, their roar.



All of this time, the sacrifices, the loss of security.



The loss of \emph{me}.



To do what?  To stop \emph{this}?



It had happened despite our attempts to the contrary.



To reconnect with my dad?



We \emph{had} reconnected.  I'd come clean about who and what I was.  We'd built up a relationship that was new, accounting for the fact that we were changed people.  Now, as I continued to fly, to put distance between myself and \emph{everything}, I wasn't sure it had been worth it.



The wind blew my hair, and I let my swarm move away, revealing the open ocean all around me.  There was only the wind and the sound of the water to hear.  The smell of salt water I'd come to miss.



My dad was gone, and I couldn't bring myself to go back and get verification.  I couldn't handle it if there \emph{wasn't} verification.



I was cognizant of the fuel gauge, of the dwindling power of the flight pack.  I knew I'd have to go back.  I knew there was stuff to do.



But I'd spent the last age trying to build towards something, to prepare for the pivotal moment.  I'd played my role, helped stop Hookwolf.  I'd communicated with Foil to urge her to play possum, tracking where the enemy was and what they could see.  It had led to us taking down Gray Boy and Siberian, trapping Jack.



And now the death toll was climbing.  Scion continued his rampage, and I hadn't even had the guts to own up to the failure.



I couldn't bring myself to go back and do something \emph{minor}.  It was arrogant, proud, but I couldn't bring myself to do search and rescue while the population was steadily scoured from the planet, the major cities wiped out like a human child might kick down anthills.



There was nothing in the worlds that I wanted more than a hug and I couldn't bring myself to ask for one.  My dad and Rachel were the only ones I could trust to offer one without further questions, without platitude or commentary, and I couldn't get to Rachel without going through the others.  My dad was even farther from my reach.



The mask I'd erected to see things through to this point was cracking and I couldn't bear to show anyone my face.



The fuel gauge ticked down.  I noted it reaching a critical point, where reaching land before I ran out might be difficult, if not impossible.



The sky was darkening.  No clouds, no city lights.  A cloud passed over sunset and the moon overhead, and it was startling just how dark things became.



A fluorescent glare cut through the darkness.  My hair and my swarm stirred.  I could feel the breeze from behind me.



I didn't turn around.



``Your call,'' Tattletale said, her voice quiet.  ``I'd like you to have my back, but I understand if--''



I shook my head, my hair flying out to either side.  I turned around and floated over to the doorway that hung in the air.



I set foot on solid ground, and felt weirdly heavy when I did.  It took me a moment to find my balance.



Tattletale caught me as the door closed beside us.  Then she wrapped her arms around me in a hug.  Odd, that she was shorter than me.  When did that happen?  I could remember her giving me a one-armed hug once, a long time ago.  She'd been just a little taller than me then.  Just the right height for a hug.  Now we were like Foil and Parian.  I was taller, receiving comfort from someone shorter than me.



I'd underestimated her.  She didn't ask any questions or offer any sympathy.



``They're all here,'' she said.  ``Ready?''



I hesitated, then spoke.  My voice was rough.  ``Ready.''



We didn't budge.  She didn't break the hug.



``\emph{Fuck}\emph{it all},'' I muttered.  My voice was still weird with emotion.  Maybe I'd keep my mouth shut at this meeting.



``Fuck it,'' she agreed.



That said, we broke apart, took a second to breathe, and then made our way into the meeting room.





