





The setup was the same, but there were undeniable changes.  More people, and just about everyone was showing up in force.



Thirteen panels, glowing lightly to light the individual groups from behind.  Each had a symbol on it, now, representing the teams.



Rachel stood at the corner at the end of the hallway, her back against the panel.  Her hair was a little out of sorts, and she wore her jacket with the heavy fur collar.  With stray dog hairs sticking to every article of clothing, each individual hair and strand of fur seemed to glow luminescent.  Bastard sat beside her, and his eyes reflected the same light.



We entered the booth as a group, Tattletale leading the way, with Rachel falling into step beside me.  We settled into a similar formation as we joined the others.  The booth was framed by a railing, same as before, but there was a crescent-shaped desk on our side of the railing.  Tattletale had already laid out handheld devices, a phone and several documents.



She took her place at the center of the desk.  Our spokesman, apparently.



I glanced over my shoulder.  The others were present, Parian and Foil included.  Grue's presence made for a dramatic effect, tendrils of his darkness coiling around the base of the panel.  He was making himself larger, moving the tendrils more.  It signaled a higher degree of emotion.



The logo was the name of the team, drawn out like a gang tag.



I took a deep breath, then looked over the rest of the room.  The other booths were crowded as well.  Every face was shrouded in shadow, the groups lit only by the glowing panels behind them.



It pissed me off.  I was \emph{surprised} at how much it bothered me, at the \emph{vehemence} of the emotion, the impulse to act, to \emph{react}.  To yell at them and call them all \emph{imbeciles}, because they were busy trying to protect their identities and be secretive when that was the lowest priority right now.



I managed to make myself stay still, instead.  If I was a little unhinged right this moment, then I needed to be calm, logical.



It wasn't really working.  I couldn't keep that sense of outrage over this trivial thing contained.  I settled for channeling it into my swarm, having them crawl in a slow rotation over me, flowing over and around one another.  It was the equivalent of drumming my fingers or pacing, if somewhat more mental than physical.



It barely helped.



Cauldron was present.  Doctor Mother stood behind their desk as Tattletale stood behind ours.  Contessa and the man Tattletale had identified as the Number Man stood with her.  Our god damned \emph{accountant, }from our supervillain days, a major player in Cauldron.  They'd managed our bank accounts, just like they'd controlled virtually everything else from the shadows.



Chevalier was here, alongside Revel, Exalt, Golem and various team leaders from the Protectorate and Wards programs.  I saw the dirt, dust and bloodstains.  I looked as bad as they did.  Chevalier had laid his cannonblade across the curved railing, and the elaborate, heavily embellished weapon served to help frame the group.  The Protectorate logo marked the back of the panel.



I looked at Golem, and he averted his eyes, very deliberately turning his attention to the other groups around the perimeter of the room.  Was he ashamed?  Angry?  I couldn't parse it.



The Guild, with Dragon absent.  Narwhal stood beside Defiant, both of them ridiculously tall.  Masamune stood beside them, not old but still stooped and frail, with a thin beard.  A D.T. soldier stood by the man.  I could guess which soldier it was.  The Guild's icon, the spear-pole with the ribbon-like flag flowing from it, marked the panel.



``\ldotsand I'm not going to appeal to emotion,'' Defiant was saying.  ``I'm not going to tell you how brave she was, how selfless and noble.  You were watching us, before you pulled the plug on her.  I know that, and I know you saw all that.  No.  You don't care.  So I'm going to talk about the facts, \emph{Saint}.  You're failing.''



Saint, standing in the booth opposite the Guild members, had been ignoring him, focusing on a computer as he typed ceaselessly.  At those last two and a half words, Saint paused for a fraction of a second.  The other Dragonslayers were situated at either end of the crescent-shaped desk, seeing to their own tasks.  The woman glanced at Saint, and that seemed to be enough to remind him to get back to the typing.



``Dragon could evacuate.  She could minimize damage, manually control the forcefields instead of relying on automatic overrides.  New York's forcefields went up too early.  Golden beam sheared through, knocked it down.  A third of the city gone.  Dragon would have succeeded, you \emph{failed}.  Two point two million estimated deaths.  I want you to know the numbers.  I want you to be aware of every single one of those deaths.  Believe me, I'll remind you, and I'll make sure everyone else knows as well.''



Saint reached up to his helmet for a second, then dropped his hand back to the keyboard.



``France-''



``Don't bother,'' Tattletale said.  ``He muted you.''



Defiant stopped talking, setting his hands on his spear instead.



All of the other major players were present, minus the Birdcage contingent.  The Thanda had six members in near-identical robes.  Their logo was a block of letters arranged in a five-by-five grid.  Moord Nag had a ring of skulls around a black circle.  Faultline's crew had a wavelength, like a reading on an seismic monitor.



Looking at them, I was startled to realize Dinah was in the group, standing right beside Faultline.



Which didn't parse.  I turned my head to look across the room at another little girl.



There was a nine emblazoned on the panel, well above her head.



I glanced back at Grue, saw how he was deliberately looking away, and connected the dots as far as \emph{why} he was withdrawn and generating more darkness.



``We\ldots'' I started to speak, and found the pitch of my voice to be a little skewed.  Quiet, I continued, ``We invited \emph{Bonesaw}?''



``Cauldron did,'' Tattletale said.  ``Hard to see, but she's restrained.''



``That doesn't make me feel any better.''  Custom made organisms could erode metal or break glass.  She could have a breakable capsule that released a plague throughout the room..



``No,'' Tattletale said.  ``But Cauldron okayed it.''



``Fuck me,'' I said.  My bugs stirred in much the same way Grue's darkness was.  It wasn't enough of an outlet.  I settled for gripping the railing in front of me.  ``Fuck \emph{them}.''



``Do you need to leave?'' Tattletale asked, her voice just as quiet as mine.  ``I could send Rachel with you.''



I shook my head.



No.  I was pissed, but I wanted to stay.



What the hell was \emph{Grue} experiencing?  This was the girl who had cut him open and spread the still-living contents of his body around a walk-in freezer, complete with augmentation that would allow him to experience pain on a level that a normal human couldn't.



For kicks.  Because she was \emph{curious}.



We were joined by a group of the Y\`{a}ngb\v{a}n, in flowing uniforms that fit somewhere between martial arts outfits and army gear, with masks like multifaceted gems.  Faceless, with only numbers to identify them.  There were capes I knew to be the Elite: Nonpareil and Patrician, Agnes Court and Blueblood.  They were the opposite of faceless, taking great pride in their appearance and their powers.  The Elite were an organized crime syndicate, shutting down anyone who tried to use their powers for profit, unless those people worked for them.



I recognized Adalid, a South American cape, hero to the people, alongside \emph{Califa de Perro}, who had one foot propped up on the desk, an elbow resting on his knee.  There was a man I assumed to be an interpreter beside them.  The representatives of the Suits were present as well, each with costumes stylized after different card suits from the original and newer decks – heart, club, spade, diamond, sword, wand, coin and cup.



I was surprised to see them.  The Suits were capes from the United Kingdom, and the United Kingdom had been obliterated.  The leader of the Hearts, Swords and Cups weren't present, leaving me to assume they were among the ones who hadn't made it.  The Suits managed different duties, classifying capes into groups for public service, fighting, intrigue, fast response and watching for malfeasance in other areas of the public.  I'd read the PRT's pages on them when I'd been investigating possible vectors for the end of the world, only to discover that the Suits were barely treading water as a group, in terms of funding and membership.  Too many deaths to Endbringers, even before the pace had picked up, and the merchandising wasn't working out, with the group accepting handouts from the PRT on a regular basis.  Not exactly the image they'd given to the public, of an elite group that was hipper, cooler and more effective than the King's Men.



The King's Men hadn't made it, I noted.



The three blasphemies were standing at one booth, young women with masks depicting ruby-lipped faces, a smile, a frown, a snarl.  Alabaster white skin, white hair, white flowing dresses.  The frowning one held hands with the other two.  They were silent, still, and their very presence seemed to be bothering the nearby Suits and Protectorate members.



The final group was arriving, stationing themselves opposite Cauldron.  I glanced up at Cauldron's icon, marking the upper half of the glowing panel – a stylized `c', tilted upward at a forty-five degree angle.



That same mark, in different sizes and at different angles, marked the various members of the new arrivals.  Weld's Irregulars.  Weld had altered his look, a little more edgy, a little less human.  Segments of his metallic flesh stood out like horns or scales, and the veins and crevices were deeper.



Strangest of all was that he was \emph{wearing} another of the case fifty-threes, in addition to his thick canvas pants.  Tendrils encircled his arms and legs, wound around his fingers.  Loops of metal, in turn, bound the tendrils, locking them into place, or helped direct them into and through his limbs.  All of the tendrils led to the same point, to a pale girl's face, with Cauldron's mark on her cheekbone.  She had no body I could make out, no hair, only the tendrils.



I saw Gully, standing a little taller than she had the last time I'd seen her in person, a muscle-laden young woman with braided hair that trailed on the floor.  Sanguine, with red hair and red skin.  Gentle Giant, a placid-faced young man who stood head and shoulders above even \emph{Gully}, and innumerable others.



The moment they were settled in, their icon appeared on the screen above them.  A three-fingered hand.



``We're all here,'' Doctor Mother said.  Civil, pleasant, unruffled even though the world was being dismantled.



Weld wasn't so inclined to be polite, nor was he unruffled  He spoke with a harsh tone that overrode his faint Boston accent, ``I'm trying to think of why I shouldn't tell my Irregulars to murder you three right here.''



The Doctor didn't reply.  She met his stare with one of her own.



The tendrils around Weld's body tightened to the point that they bit into the metal.  I saw some people shift position



He continued, ``I know what your \emph{Contessa} does.  I know about Number Man too.  Hell, we know about the ghost girl who keeps you company.''



``We call her the Custodian.''



``Is she one of your mistakes, like us?''



``Yes,'' the Doctor said.



``And did you brainwash her to keep her servile?''



``No.  For one, she has no brain.  Is this really necessary, Weld?''



Weld didn't show a trace of hesitation.  ``I think it is.  Everything seems to tie back to Cauldron.  To you.''



``You're blaming us for this.''



``You're the most likely culprit,'' Weld said.



``No,'' the Doctor replied.  ``Our issue here is a lack of information.  We have four sources that can corroborate the same story.  One of those sources is in the Birdcage, where they'll remain until we decide it's time to free them.''



``There's Bonesaw, who isn't our most reliable source, and I'm guessing Tattletale is the fourth,'' Weld answered.  He saw the Doctor respond and nodded a little.  ``Convenient.  For those who don't know, the Undersiders got their start working for Coil, who was linked to Cauldron by two degrees of separation at \emph{most}.''



``You \emph{have} done your homework,'' Tattletale said.  ``But no.  No ties to Cauldron here, aside from the rare clandestine meetings where we do rock-paper-scissors to figure out who plays a big part in the latest Endbringer attack.''



Weld shook his head a little, and then turned his attention to the Doctor.



I didn't hear the question but a large part of that was the fact that I wasn't listening.



``You knew?'' I asked her.



``No.  I only figured it all out just before it happened,'' Tattletale murmured, not taking her eyes off Doctor Mother.



``But \emph{they} knew?''



``Yup.  Marquis did too, but they told him to stay quiet.''



I clenched my fists.



No.  I wasn't going to be able to suppress this.



I could leave, stalk from the room.



Except why the fuck should I?  To spare these people's sensibilities?



``You knew,'' I said, interrupting Weld's angry monologue about Cauldron's monstrous parahumans.  I spoke loud enough for everyone to hear.  I didn't care anymore.  ``You \emph{knew} Scion would do this?''



Doctor Mother looked my way.  ``Yes.''



``And you did nothing.  You stood back and you let this happen,'' I said.  I was aware that every set of eyes in the room was on me.



``It's better that this happens now.  From what we know- and I do want to express that I'm eager to compare notes with the other parties- it was inevitable.  Now or later, Scion was going to go rogue.  If we waited until a decade had passed, we might not have the numbers or the powers we have now.''



``You \emph{knew},'' I repeated myself, staring at her.  ``We could have put this off.  Bought ourselves time to deal with other crises, to find an answer, a way to stop him or\ldots''



I trailed off, lost for words.  \emph{To stop him.  That's enough.}



``We did try,'' the Doctor said.  ``We offered as much assistance as we could without hamstringing ourselves for the next part of this.''



The Number Man spoke, ``All of the statistics point to a decline in population over the ensuing few years.  We were already in the midst of the breaking point. You experienced much of that yourself, Undersiders.  Enough capes in one place, and it becomes the equivalent of nitro waiting to blow.  Brockton Bay wasn't managed quite so well as other clusters like New York or New Delhi.''



He gestured towards Chevalier, then the \emph{Thanda} as he named the cities.



He continued, ``You yourself took part in the chain reaction of events that followed the attempted ABB takeover.''



I didn't move.



``Cause and effect.  A local gang leader by the name of Lung was arrested by Armsmaster, the leader of the local Protectorate team.''  He paused very deliberately, very \emph{knowingly, }before continuing, ``A subordinate member of the gang goes on a rampage, escalating violence and forcing another local cape to advance his plans for taking over the city.  He already has the very talented Dinah Alcott, and he recruits the Undersiders and the Travelers to remove enemies from the board and bring them into his camp.  The latter group of heroes sets the seeds for a later fiasco, the Echidna event.  Conflict and the dormant Echidna's presence lead to Leviathan attacking, which leads in turn to the Nine visiting.  I could go on, naming the Undersider's actions in regards to seizing the city and stopping Coil, but you know the story.''



``You're saying all of that stemmed from one arrest,'' one of the female members of the Suits said.



``No,'' the Number Man said, and he managed to sound only a \emph{little} condescending.  ``I'm saying that parahumans as a whole are chain reactions waiting to happen, and we were already approaching a critical point.  Every year, the percentage of parahumans in the population increases.  At that same time, the odds of a cataclysmic event happening \emph{somewhere} are increasing steadily.  Imagine a situation like the Echidna event that turned out \emph{more} unfavorably, or a Nilbog who wasn't content to stay in one place.  We have the blasphemies, Sleeper, and the Ash Beast, even the Slaughterhouse Nine, all as living examples of this concept at work. The world already stood on a precipice, and I'm not even mentioning the Endbringers in all of this.''



I glanced at the blasphemies.  They hadn't moved an inch, even as they were mentioned.



The Number Man paused.  ``There was an exceedingly good chance that we would have only sixty-six to twenty-five percent of the forces available if we waited ten years.''



``Fourteen years from now was the breaking point,'' Dinah spoke up.



``Fifty-three to two percent of the forces available, then,'' Number Man responded.



``Yes,'' the Doctor said.  ``We weren't helping it along, but we're not overly upset.  In fact, we consider this a best case scenario.''



I saw Contessa tense even before my swarm moved, expanding, drawing out lines of silk-



A slam interrupted me, jarring me back to reality.  I turned to look at Chevalier.  He'd struck the desk in front of him.



``Don't,'' he said.  It took me a second to realize he was talking to Doctor Mother.



``A poor choice of words,'' the Doctor said.  ``What I mean to say is that a very large number of powerful capes remain active and alive, ready to combat the threat.  We're situated to respond to this \emph{somehow, }both offensively and reactively.  At this very moment, we are managing a large-scale evacuation.  We consider it a priority to keep Scion unaware, so we are evacuating the landmasses on the opposite end of the globe in hopes he won't be able to respond or act.''



``Evacuating people like you did in New Delhi?''  Tecton asked.



``Mm.  No.  Different earths, closing portals behind us as we go.''



One of the Thanda spoke, ``Then you were capable of this evacuation before?  Moving hundreds of millions to safety?''



``Yes,'' the Doctor responded.



``\emph{Why}?'' he asked.



``Because of Scion.''



``Because you \emph{knew},'' I repeated myself for the third or fourth time.  My fists were clenched.  ``You had an idea this was going to happen.''



``Yes,'' she said.  ``Everything we've done has been to build towards this eventuality.''



A silence hung in the air.



I looked over the room.  Moord Nag and the South American capes had interpreters rattling off the particulars of the conversation.  The Protectorate, the Irregulars, Faultline's crew, the Suits\ldots all bristled with anger.



Hell, I did too.



Faultline spoke, ``So.  It all comes down to this.  Millions or billions die and you get to step in now and be the big damn heroes.''



``We have no intention of doing so.  In truth, as much as we've stockpiled countermeasures, gathered information and planned ahead, we fully expect to fail.''



``Fuck,'' Tattletale muttered, just beside me.



``All of the war crimes, kidnapping people, human experimentation, creating monsters, creating \emph{psychopathic }monsters, letting millions die\ldots and you think it's for nothing?''  Faultline asked.



``It's very, likely,'' Doctor Mother said, unruffled.



``Then \emph{why}?'' Weld asked.



``Because we decided in the very beginning that we don't want to be left wondering if we could have done more, in the moments before humanity ceases to exist,'' the Doctor said.  ``Why did we make you into what you are, Weld?  Because it was an option, a step forward.  Why did we keep it secret?  It improved our chances.  Why did we not tell you about Scion?  Because it improved our chances.''



I stared down at the roughly circle-shaped patch of darkness in the center of the room.  ``You made sacrifices, you made sacrifices on the behalf of others, and you made the hard calls, but it was all for something greater.  I bet you think you won't have any regrets at the end.''



``It's been some time since I lost sleep because of a heavy conscience,'' the Doctor said.



Weld gripped the railing hard enough to make the wood splinter explosively.



``I know what that's like,'' I responded.  ``I've walked down that road.  Maybe not so ugly a road, but I've gone that route.  All the way along, I told myself it sucked, but I wouldn't do it differently.  I did everything I did for a reason.  Except now, having reached the point I was working towards, I finally do regret it all.  The last two years, the way I treated my teammates, leaving the Undersiders\ldots I'd change it all in a heartbeat.''



I turned my eyes to Golem, then the Undersiders, and then to Doctor Mother.



``Maybe I will regret it,'' the Doctor said.  ``But I'll run that risk.  If the world ends regardless of our efforts, the only one left to judge me will be God.''



I shook my head a little, but I didn't answer her.  We'd dragged this on long enough.



She seemed to agree.  ``Let's talk about the situation.  Tattletale, if you would?''



``Me?  I'm flattered.  Let's see\ldots Scion isn't human.  All of our powers stem from the same source.  It's this big alien bastard that we keep seeing when we have our trigger events.  Except each of his cells is coded with just a fragment of his brain and a technique he uses to manipulate his environment, protect himself or attack others.  He spread powers around Earth as part of a way to stress test them.  He wants to leverage \emph{our} brains and imagination to figure out ways to make the most of these abilities or innovate new ones.  With me so far?''



``No,'' Gully said, from her spot beside Weld, ``Not at all.''



I nodded my head in silent assent.  Not that I didn't \emph{understand.  }It was just a lot to take in.



``Okay, well, it gets worse, so follow along.  After distributing all of the powers he could, he left a chunk of himself still active, still alive, and he kept all of the good powers, the abilities he needed to ensure this whole process continues.  Except something went wrong, and the process is fucked.  How am I doing?''



``Minor errors,'' the Doctor said, ``But roughly on target.''



``Great!''  Tattletale's grin was visible in the gloom.  She rubbed her hands together, clearly enjoying herself, despite the circumstances.  \emph{She wanted a scene where the detective reveals it all.  This is just\ldots a little weirder}.  ``Okay!  Let's see.  The process is fucked, and he's a daddy with no little ones to take care of.  They're dying or dead or something else went wrong and he's been looking for a purpose.  He got that purpose when a guy called Kevin told him to go help people.  He got a \emph{new} purpose when Jack told him to start murdering.''



\emph{Murdering}.



My dad's face crossed my mind.



The dead I'd had to ignore while rescuing others were a jumble, too numerous for me to even piece together in my mind's eye.



``If it were mindless destruction,'' the Doctor said, ``It would be acceptable.  We could convince him to abandon this, or hope he burns himself out on \emph{this} Earth's remaining inhabitants, after we evacuate everyone we can.  There's another problem.''



She touched something on her desk, and the various panels behind each booth \emph{changed}.  They were video screens, three times as tall as they were wide, and each showed the same clip of Scion's rampage.



``United Kingdom, first target struck.  Obliteration,'' the Doctor said.  ``Eastern coast of Canada and the United States, damaged, but casualties were a third of what they were in the initial strike.''



She paused.  Faultline took the opportunity to interject, ``Not following.''



``The third attack was against Mali, followed by Burkina Faso, Ghana, Togo, and all down the coast of Africa.   In this attack, he selectively murdered specific individuals.''



I watched the scene.  Scion flying with a speed like an arrow shot from a bow, narrow lasers blasting from each hand.  He came to a stop a short distance from the camera, canceling the laser assault.  The image panned over to look at the city as Scion hovered there in the sky.  A major population center.  Capes were already taking flight to stop him.  No, not capes.  People in civilian clothes with powers, many heavily tattooed.



He glowed, and the glow flared.



The camera dropped a short distance and struck something solid.



``That blast we just saw,'' the Doctor explained, ``Was a calculated strike.  The city was left mostly intact, but Scion killed specific people, targeting anyone who had already hit puberty.''



``How?'' Tattletale asked.



``His perceptions are finely tuned,'' the Doctor said.  ``He's aware of his immediate vicinity, and in absolute control of how his power is expressed.  He left\ldots what was the number?''



``An estimated four hundred and thirty thousand,'' the Number Man said.



``Four hundred and thirty thousand orphans.''



\emph{He didn't kill them all}.



\emph{Why is that scarier than the alternative}?



``In Russia, his beam started fires.  He cut off every escape route, then began setting fires from the outside in.  It took him thirty-five minutes to start the fire, and he waited for fifteen minutes while the flames spread and everyone within was cooked.  Heroes that attempted to stop the attack were killed.''



``He's experimenting,'' Tattletale said.



The Doctor nodded slowly.  ``Following a very distinct formula.  He's reversing what he did at the outset.  Saving children, stopping fires.  The man who initially gave him the orders is hospitalized, or we'd ask about the instructions he provided.  It might give us an idea of what Scion is going to do and the patterns that might emerge in the course of this\ldots experimentation.''



\emph{Experimentation.}



He didn't have to learn to be dangerous.  He was capable of obliterating us all in a matter of days.



``We're bringing the girl who was in contact with Scion here,'' the Doctor said.  ``Provided she survives.  Scion is too close for us to access her at the moment.''



``I only want to know two things,'' the Dog King said.  ``What do we do, and how do I protect my people?''



There were nods from around the room.  I found myself joining them.



At the simplest level, that was what we all wanted.



Those of us that weren't monsters, anyways.



``We run,'' the Doctor said.  ``Save as many people as we can.  Muster your forces.  Strategize, think outside the box.  If you have ideas, run them by the group.''



``Let me start, then,'' Faultline said.  ``Simple answer.  Talking to him got him to be a hero before, and talking to him made him do \emph{this.  }Let's talk to him again.''



``And say what?''  Tattletale asked.  ``Stop, pretty please?''



``No,'' Faultline retorted.  ``I want to find another option.  We've got a planet full of thinkers and tinkers, let's gather intel, figure out just what it is he wants, and see if we can provide it.  Get him to \emph{leave}.''



``It's not that simple,'' Tattletale said.  ``That faerie kook who's going on about queen administrators and all that crap?  She was a big hint in \emph{me} figuring this stuff out, and she's under the impression that this all ends with this Earth and every \emph{other} Earth being obliterated.  We don't want to give him what he wants.''



``Then we trick him,'' Faultline said.  ``Before he gets too clever and before he wipes us out.  Tell him to, I don't know, fly to the edge of the known universe and back?''



``You try that,'' Tattletale said, injecting a note of sarcasm into her voice.  ``That sounds \emph{brilliant}.''



``Any idea is a good thing,'' Chevalier said.  ``We'll emphasize protecting and preserving the people we can save.  Can you give us access to your portal network?''



``Yes,'' Doctor Mother answered.  ``Of course.  We'll be observing you at all hours.  You only have to ask for a door and we'll connect you to our central hub, provided you aren't on the same continent as Scion.''



She took a deep breath, then sighed audibly.



``I don't ask you, \emph{any of you}, for your help.  I don't ask for your assistance or cooperation.  I only want us to share resources, provide solutions.  Contessa, if you'd please ungag Bonesaw?''



Contessa nodded, then strode across the room.  She worked something away from Bonesaw's face, then returned to Cauldron's booth.



``Hello,'' Bonesaw's voice was eerie, childish in a way Dinah's wasn't.  She craned her head around, clearly unable to move anything below the neck, looking at the panel behind her.  ``I'm not with them.  Honest to gosh.''



``There's no reason for her to be here,'' Defiant said.



``There is,'' the Doctor said.  ``Contessa believes it is the most economical way to get what we need.  Tattletale?''



``I'm really having mixed feelings about that whole `Tattletale' thing you keep doing,'' Tattletale responded.  ``It's like calling for your dog, which is irritating, but you keep giving me chances to do awfully fun stuff.  You want me to dismantle Bonesaw?''



``Feel free,'' the Doctor said.  ``Our goal is a remote.''



``I'm playing nice now,'' Bonesaw said.  ``Promise.''



``Gotcha,'' Tattletale replied to the Doctor.  She turned to the little girl.  ``So.''



``This is cheating,'' Bonesaw said.  ``I'm not trying to be tricky or anything.  I just want to stay alive, help out.  I don't want the world to end.  The remote's just collateral.  Once I give it up, you have no reason to keep me around.''



``Which is,'' Defiant commented, ``Exactly what you'd say if you were Jack's sleeper agent, biding your time to deliver the worst possible attack at the worst possible moment.''



``No,'' Tattletale said.  ``She's being honest.''



``\emph{Honest}?''



``The murderous little tot had a change of heart.  A \emph{partial} change of heart.  Let's be honest.  You're not going to turn away from the \emph{art} of your powers that easily, are you?  You'll still crave to do something interesting, and maybe that \emph{interesting} is at the expense of others.''



``It can be at the expense of bad people,'' Bonesaw said.  ``Does that work?''



``No,'' Chevalier said, Defiant echoing him by a half second.



``Besides,'' Tattletale said, ``The only bad person that concerns us is Scion, and you can't touch him.''



``Phooey.''



``Drop the act,'' Tattletale said.



There was a pause.



A voice that wasn't nearly so childish, so perky, sounded across the room.  ``Okay.''



``Better,'' Tattletale said.  ``You're in the middle of a metamorphosis.  Something triggered that change.  Love?  No.  Friendship?  \emph{Friendship}.  Someone outside the Nine.''



``Yes.  It's not that big a deal.  I realized Jack's been playing me because \emph{that} woman,'' Bonesaw jerked her head in the direction of the Doctor, ``\emph{fucked} with my head.''



``Which is why I'm handling this and not her, I guess.  And because this little show builds the idea of solidarity between our factions.  Multiple goals, I'm sure.''



``An illusion that's strained when you mention it to everyone present,'' Doctor Mother commented.



``Whatever.  Bonesaw.  Boney.  Bones.''



``Riley.''



``\emph{Riley}.  You're going through some \emph{changes}.  Let's-''



``Can we cut the jokes?'' Chevalier asked.  ``There's a lot going on out there.  We've wasted enough time already.''



``Then \emph{go},'' Tattletale said.  When he didn't budge, she added, ``I'm having a conversation with \emph{Riley} here.  She's figuring out who and what she is, and we've got a bit of a snarl.  Her \emph{art}.''



``My power.  That's all it is,'' Bonesaw said.



``You're attached to it.  You feel a bit of pride in what you've made, even now that you're apparently turning over a new leaf.  I'm afraid I'm going to have to tell you to get real.''



``I'm not that attached.  Or proud,'' Bonesaw said.



``Sure you are.''



``No.  I mean, like, I think about my friend and I imagine messing with him and it's like\ldots I don't want to do that.  I enjoy his company.  So I think about the other people and put his face over theirs and-''



``And you still do horrible things.  Let's not pretend you weren't screwing with Nilbog or palling around with the rest of the clones.  You made them possible.''



``I had to.  I-''



``Chevalier was right.  We don't have a lot of time.  Stop equivocating and \emph{listen}.  You're a monster.  Maybe the worst one out there.  But when it all comes down to it, you're just like that big golden bastard out there.  You're Jack's pawn.  Everything you ever made, everything you ever did, the strongest parts of you, the little vulnerabilities, custom tailored by him.''



``No,'' Bonesaw said.



``\emph{Yes}.''



``The friend I made, this new me, it's-''



``Calculated.  By Jack.  Don't tell me he doesn't plot things for down the road.  Hey Golem, talk to me.''



Golem's voice sounded from the other end of the room.  ``What?''



``You thought Jack had a thinker power.  Why?  What?''



There was a pause.



``Because he's like Weaver.  He reacts like someone that is way too aware of what's going on.''



\emph{Acts like me?}



I'd made the comparison myself, but I'd tempered that, held back as I formed that conclusion.  Hearing it in such a blunt way stung as much as a slap in the face.



``And you sent in the D.T. guy because-''



``Because Weaver surrounds herself with bugs, and Jack surrounds himself with capes.  The non-cape is the only variable we haven't seriously tried.  The \emph{competent} non-cape.''



Tattletale nodded, ``Thought so.  So let's think about that.  He's got a thinker power that lets him manipulate parahumans, or read them, or gauge how they'll react.  He uses it, probably unconsciously, to constantly maintain the edge.  And he gets \emph{bored}.  You've seen him get bored, haven't you, \emph{Riley}?''



``Yes.''



``\emph{Yes}.  And when he gets bored, he sets up scenarios like the game in Brockton Bay, the test with Golem coming after him, whatever else.  It usually falls apart before it comes to a head, because Jack is chaos incarnate, people cheat, \emph{Jack} cheats, and so it goes.  So tell me, do you \emph{really} think he wouldn't let you have a little slack to see how you'd operate?''



Bonesaw didn't respond.



``Yeah.  \emph{Exactly},'' Tattletale said.  ``Your art?  It's \emph{his} art.  Your power and everything you do with it, it's stuff he's shaped.''



``That's not true.  I come up with my own ideas,'' Bonesaw sounded almost defiant.  She'd also, I noted, forgotten the original message, saying her art wasn't important to her.



``His ideas.  Everything's tainted with \emph{Jack}.  And you know it better than I do.  You can think of all the little scenes and conversations.  How your favorite projects were the ones your \emph{family} applauded.  The ones \emph{Jack} praised, above all.''



Again, Bonesaw was silent, unable to retort.



``You want to face the new you?  Here it is.  It's not an easy change.  It \emph{sucks}, even.  The magic's gone, now.  Your power won't be quite so fun.  Just the opposite, maybe.''



Still, there was no response.



``This is the real change,'' Tattletale said.  ``Being reduced to \emph{nothing}, starting anew.  And you get to carry all the shit and all the hate that you earned being an unholy terror before.  You \emph{deserve} to carry all that shit and deal with the hate.  You've got a steep uphill climb, before you even get a trace of respect or trust.  You understand?  Putting your buddy's face on possible victims isn't even close to redemption.''



I could see Bonesaw's posture change, even in the midst of her restraints, her shoulders drawing forward, head hanging a bit.



Fuck me, was I feeling a pang of sympathy?  My feelings were still off kilter, undefined, unpredictable.  It was scary, like stepping off a ledge with my eyes closed, not knowing what was on the other side.  Except the feeling recurred \emph{constantly}.



Be rational.



\emph{Let's not push the lunatic too far}, I thought.  That's rational.



But Tattletale had let up a fraction.  Her questions and attack were calculated, based on cues from her power.  ``You want trust?  Give us the remote.''



``Fuck that,'' Bonesaw said.  ``Fuck no.''



``You have to trust \emph{us} before we'll trust you.  Give us the remote.''



Bonesaw didn't move.



I saw Contessa lean close to Doctor Mother.



``It's done,'' the Doctor said.  ``We'll have the remote shortly.  Thank you, Tattletale.  Next order of business is the Birdcage\ldots''



I looked at Tattletale, who was still staring at Bonesaw.



I could see Grue as well, tense, the smoke tendrils churning around him.



And Parian, her hair and frock stirring as if there was a wind blowing.  She'd lost her entire family, either to the Nine or to Bonesaw's warped plastic surgeries, making their faces identical to some of the most hated people in America.



They had derived \emph{satisfaction} from this.  An attack on someone who'd attacked them, fair and just, acceptable, not quite torture.



Not \emph{physical} torture, anyways.



I'd had my head cut open.  I'd seen Grue change, becoming a shell of his former self.  Hell, \emph{I'd} been traumatized by what she'd done to \emph{Grue}.  I wasn't about to begrudge them that.



But I still felt a measure of sympathy.



``To be clear,'' the Doctor was saying, ``We didn't invite the Birdcage residents here tonight because we knew it would be hard to impossible to send them back, all things considered.''



``And because you'd lose our cooperation,'' Defiant said.  ``Saint hamstrung us at a crucial juncture, he abandoned a number of people in this room to die when we were going after Jack, effectively \emph{delaying} us, and he's supplanted Dragon, doing a criminally ineffective job at managing her duties.  He's done all of this to free \emph{one} man from the Birdcage.  For selfish ends.  If you \emph{accommodate} him-''



``You'd intentionally obstruct us?'' Saint asked.  ``Out of \emph{spite}?''



``I promised I would kill you,'' Defiant said.  ``I will.  Anyone who allies themselves with Saint gets the same treatment.''



``I'm terrified,'' Saint said.  ``Not of \emph{you}, but of your shortsightedness.  The end of the world is nigh, and you have a vendetta.''



``I'm inclined towards tunnel vision,'' Defiant replied.  ``For now, a great deal of my focus is turned towards one task.  Denying you what you want.  There are six blocks on the Birdcage that Dragon set in place.  Dragon is incapable of opening them, because she didn't want to be coerced into doing so.  I imagine Saint is here because he wants the keys to the blocks.''



``Yes,'' Saint said.



``Then if everyone here accepts that the Birdcage should be opened to let a select few prisoners out, I will give you the key.''



Slowly, hands raised around the room.  Countries all around the world had prisoners in the Birdcage.  Countries all of the world had \emph{stories}, horror stories about the people who had been sent there and what they'd done before.



But things were dire, and we needed firepower.



I raised my own hand.



``Then I'll provide the keys.  Two stipulations.''



``I can guess what these stipulations are,'' Saint said.  ``You want to wake Dragon up?''



I saw Tattletale tilt her head at a funny angle at hearing that.



``No.  You're as singleminded as I am, and you've turned that focus towards being her enemy.  We need the access you stole from Dragon as much as we need my keys, and you wouldn't give the access if it meant helping her.  Two things.  You step down, and Teacher remains in the Birdcage.''



Saint snorted.



``No?'' Defiant asked, his voice level.



``Hardly a fair bargain.  Give me time, and I can find the keys.  It's just a matter of time before I dig through the code and find it.  You want to goad me about the lives I've cost?  Know that your stubbornness is doing the same thing here.''



``You and everyone else here just agreed we should open the Birdcage,'' Defiant said.  ``But you're the only one here who wants to be in charge, the only one here who wants to free Teacher.''



``We need information if we're going to fix this, and he's our best source of Thinkers.''



``Weak thinkers,'' Tattletale said.



``Thinkers, all the same.''



I could see Saint's head turn, the cross on his face glowing as he scanned the room, searching the shadowy figures for signs of body language or gestures, for signs of agreement or disagreement.



I could see just as well.  Nobody was jumping to agree.



His only chip was his monopoly on Dragon's technology, and he now had to choose between agreeing to Defiant's terms or refusing and making an enemy of everyone present.



``A compromise,'' Saint said.



``No,'' Defiant cut him off.  ``You're unable to use Dragon's full complement of resources, and many people in this room are aware of the fact.  Many came close to losing their lives.''



``All I want is Teacher free.  I'll step down, if you have someone to replace me.''



``There are options,'' Defiant said.  He looked to the Undersiders.



``Then that's settled,'' Doctor Mother said.  ``Select the people you want, and we'll create the doorways.''



``That would greatly simplify matters,'' Defiant responded.



``Any other business?  Suggestions?  Options?''



``Yes,'' Faultline said.  ``Again, being pretty simple here, but you guys are going way over our heads here.  If we're opening the Birdcage\ldots''



``There's less dramatic measures,'' Defiant said.  ``Amnesty?''



``In a time of crisis,'' Faultline said.



``I'll talk to my superiors,'' Chevalier responded.



``Good,'' Doctor Mother said.  ``Many of us have things to see to.  Do what you can.  Use the doorway or ask for one of us if you require it.  We'll see you all have a means of communicating shortly.''



People began preparing to leave, gathering stuff together.



``No,'' I could overhear Contessa saying, ``I ask myself several questions before I go anywhere, and one pertains to strangers.  Stay behind.''



Imp appeared next to her.  She walked back to us with a very dejected appearance.



My eyes turned to Bonesaw.  She hadn't moved or spoken.



I felt another pang of sympathy.



But not quite enough to act on it.



Not enough to forgive her, not this easily.



Not \emph{her}.



\sectionbreak



It was strange to enter a prison as a visitor and not an inmate.  Very similar in some ways, down to the pat-down, different in others.



Free to leave.  Free to wear clothing.



The place was ramshackle, an ancient building of stone slabs that had been modified to serve as a prison.  Ten inmates to a room.  Innumerable guards.



I took a seat and waited.  I didn't feel calm.  I didn't feel confident.  My feelings were still in a state of flux, and I couldn't pin them down.  I felt like I could scream or cry at any moment.



But, more than any other time, I wanted to appear confident here.



The door opened, and four guards led a prisoner to the chair opposite mine.  We were separated by a pane of bulletproof glass.



Her eyes glared at me, cold.  Not the eyes I'd known, no act, no hiding behind a mask.  This was \emph{her}.



``Hi, Shadow Stalker,'' I told Sophia.



``Taylor,'' she replied.





