





\emph{Back to the beginning.}



``Emma's dead,'' I said.



Sophia nodded.  ``Her dad told me.''



Not a trace of emotion on her face.  Not a flicker of a change in expression.  Did she not care, or was she wearing an exceptional mask?



Funny, just how easily those masks came to people.  Costumes were nothing in the grand scheme of things.  Cloth or kevlar, spider silk or steel.  It was the false faces we wore, the layers of defenses, the lies we told ourselves, that formed the real barriers between us and the hostile world around us.



Looking at Sophia, I found myself instinctively reaching for that mask.  I was using my bugs to channel my feelings, even with my concerns about my passenger and how it might be merging with me.  I was wearing that aura of indomitable calm, even though I wasn't sure I liked the Taylor of this past year and a half, who had been doing just that as a matter of both habit and necessity.



The two of us, in this shitty little makeshift prison.  Tattletale had had this place built ahead of time, with the idea that we might need secure storage or a prison for anyone who made trouble in Earth Gimel.  Too little, even with the measures being taken.  Those with less than six years in their sentences were being given a limited release and kept in a more isolated location, with family and friends free to join them.  The only exceptions to that early release were the parahumans.



Maybe there was a human rights violation or a lawsuit in there, but the people in charge had other concerns.



My phone buzzed.  I picked it up and looked at the screen.



Japan hit.  V. little left.  Most evacuated.  22m est. dead.  Total est. toll 500m.



``PRT issue phone,'' Sophia commented.  ``Newer model than the one I had.''



``Yeah,'' I answered.  I put the phone down on the little ledge beneath the bulletproof glass.



``Big bad Weaver.  That's what you go by now, isn't it?''



``I prefer Taylor.''



``\emph{Taylor}.  Made it pretty big, as capes go.''



I shrugged.  ``Wasn't really a priority, in the grand scheme of things.  I only wanted the power so I could do what needed doing.''



``Never appealed to me, power in the greater sense,'' she said.  ``Personal power?  I always paid more attention to power on a one-on-one level.''



I let myself relax a little.  We had something to discuss.  It wasn't going to be a fight, a series of attacks.



``I guess,'' Sophia said, ``You took my lessons to heart.  Used what you learned from our little\ldots what's the word?  Lessons?  Made something of yourself after all.''



\emph{She's taking credit?}  I was a little stunned, the mental gymnastics she must have managed to do that\ldots \emph{what?}



A small smile touched her lips.  Smug, superior.  I'd seen it enough times in my interactions with her.



``Mark on your cheek is gone, where I gouged you.''



``I think it disappeared at some point when I got healing or regeneration.  Grue or Panacea or Scapegoat.  Don't know.''



``Mm,'' she said.  Her eyes were studying me, and the look wasn't kind.  ``Your family make it out okay?''



Just the question was like a slap to the face.



``No,'' I said.  ``I don't know.  Haven't bothered double checking or asking.''



``Me either,'' she said.  ``Not that I'm really in a position to go look for answers.  But they weren't visiting much anyways.  \emph{Token} visits, you know?''



``I don't, really,'' I said.  ``My dad was pretty cool after I joined the Wards.  We didn't see each other as much as I maybe wanted to, but it didn't feel like token visits.''



``Difference between you and me,'' she said.  She glanced over her shoulder at the guard behind her, then planted a foot against the little ledge beneath the bulletproof glass.  Her hands, handcuffed, settled in her lap.  ``Your daddy cared.  You know, that meeting where you tried to get us that in-school suspension?  I was more pissed at the fact that your dad was there than the suspension.''



``Then the woman was-''



``A PRT twit.''



I nodded, but I was distracted from my response by another vibration of my phone.  I picked it up to look at it.



Mordovia bubble hit.  Sleeper has been roused, last tracked en route to Zayin portal.  Casualties unknown.



``World's really ending?''  Sophia asked.



``Yeah,'' I said, putting the phone back down.  ``Scale, damage, repercussions, all worse than any Endbringer attack.  They're predicting that maybe five hundred million are dead already.''



The mention of half a billion people being dead didn't affect her more than the mention of Emma's passing.  Not visibly.



``Too bad,'' she said.



``There's no going back,'' I said.  ``We're preparing for a counterattack right now.  We'll see what works, what doesn't.''



``He beat Behemoth,'' Sophia said.



``I know.  I was there,'' I said.



She looked annoyed at that.  Her eyebrows drew closer together, and she shifted position, putting both feet up on the little ledge, one ankle crossed over the other.  It was only after she was settled that she responded, ``He beat Behemoth, and nobody could manage that.  He's \emph{stronger}.''



``We'll try anyways,'' I said.  ``I don't think any of us are prepared to roll over and die just yet.''



``Dumb,'' Sophia said.  ``Throwing your lives away for nothing.''



``The alternative isn't any better,'' I said.



``What?  \emph{Not} fighting?  Finding a good spot in another dimension to hide out?  It's a \emph{thousand} times better, Hebert.  We're like cockroaches in the face of this asshole.  You know what happens if we line up and march off to die single file?  The strongest of us die, there's nothing left to protect the others and humanity gets wiped out.  No.  Fuck that.  Cockroaches survive because no matter how hard you try, they're numerous enough, tough enough, and spread out enough that a few of them always survive.  They survive the predators, the poison, the fire, the radiation, and a few generations later they're back in full strength.''



``Yet you fought Leviathan.''



``I fought Behemoth too, few months before.  Kind of.  Mostly did search and rescue.  Difference between \emph{that} and \emph{this} is that we're more like rats when going up against a fucking Endbringer.  We're vermin in comparison to them, but we're vermin that can take bites out of them.  Get enough rats together and they'll take down a human, no matter how well equipped that human is.''



``But cockroaches can't?''  I asked, with a note of irony.



She gave me a look that people typically reserved for when they'd been spit on.  ``Don't try to be clever, Hebert.  It doesn't suit you.''



I rolled my eyes.



``I'm speaking metaphorically.  It's a\ldots what's the word?  Like a ladder.''



``Hierarchy.''



``Hierarchy.  Yeah.  Scion's one step above the Endbringers.''



``Couple of steps,'' I said.



``A \emph{couple} of steps.  Whatever.  So you've got to evaluate that shit, understand?  Where the fuck do we stand in relation to \emph{him}?  Rock bottom.  How do we deal?  We scatter.  Spread out far enough apart.  One guy can't murder all of us if we can find a way to spread out over a million different earths.  Stick to villages and shit.  Whatever.''



I was somewhat caught off guard by that.  It wasn't a \emph{bad} plan.  Defeatist, but not bad.  Something we'd implicitly settled on in the meeting, though we'd also agreed to keep our mind open for options.  I was getting a chance to see how she parsed the world, if maybe she had been influenced by her passenger like I was by mine, and I was seeing a philosophy that she seemed to value.



It was an insight into \emph{Sophia}, and it wasn't one that matched up with my expectations.



I ventured, ``And here I thought you were more focused on being superior to others.''



Sophia shook her head, her lip curling up a fraction.  ``I acted superior because I \emph{was} superior.  Still am superior to most.  That comes with \emph{perks}.  Do what you want, get away with shit, get people to look past the stuff you want them to look past.  What you've been up to, I bet you've done that.  Leveraged power?''



``Leveraged power,'' I said.  ``Yes, I have.''



``Because you're better.  You're a little arrogant, maybe?  A little less forgiving of mistakes?''



``I \emph{was},'' I said.  ``Thing is, when it came down to it, I wasn't stronger or cleverer because of it.  It wasn't an advantage in the critical moment.  Maybe the opposite.''



She dropped her feet to the floor and leaned forward, folding her arms on the ledge, her face not even an inch from the glass.  ``But it got you that far.  Others there, and they couldn't fix it either.  Not a reason to change your mind.''



``It was a pretty important moment,'' I told her.  ``\emph{The} most important moment.  But I wasn't in the right place, wasn't in contact with the right people.  More than anything, I wasn't asking the right questions.''



She looked profoundly disappointed.  ``See, now you're just being a whiny bitch again.  \emph{Negative}.''



``Retrospective,'' I said.  ``Figuring out what I did wrong, changing.''



``Your biggest problem, Hebert, is that you never realized your place.  I \emph{almost} had respect for you.  Hard not to, when you're pretty much copying me.  But you're still waffling on shit you shouldn't be waffling on.''



Copying her.



I'd admitted to taking lessons from Bakuda, from Jack.  I'd picked up some of Purity's protectiveness, only I'd turned it towards my territory.  I'd learned from Coil, from Accord, and yet Sophia saying this nettled me.



I knew why, and it \emph{wasn't} because I felt like she was eerily on target.  No, it was because it was an out for her.  An excuse, a justification that let her keep her tidy little worldview.



The best revenge was supposed to be living well, but maybe there was a petty fragment of my psyche that wanted to rub it in her face.  Not that I \emph{was} living well.  The situation was catastrophic, my dad was dead, and I wasn't sure where I stood.



I looked down at my gloves.  They were dark gray, but they'd been caked in blood, and even a good washing in cold water had failed to get them thoroughly clean.



``Sophia,'' I said.



``What?'' she asked.  She leaned back in her chair.



``They're opening the Birdcage.  Letting some of the scarier criminals out, in the hopes of getting some assistance against Scion.  There's a lot of good firepower in there.''



``Uh huh.''



``Doesn't make sense to go that far if we don't extend the same concept to a smaller scale.  Not sure what the numbers are, but there's a hell of a lot of possible recruits there.''



``And you're here because, what, you're going to recruit me?''



I ignored her.  ``Problem with this situation is there's no good way to keep track of all of this.  In the chaos, it's hard to manage records, and time's tight enough we're not going to be able to pull a review panel together.  So how do you decide who gets to go free?''



``What a good question,'' Sophia said.  She met my gaze with a level stare.  Not a glare anymore.



``Capes interact most with other capes.  Smaller pool of people to find, contact and question, versus trying to hunt down civilians who might know so-and-so.  It's not a perfect method.  It's flawed, even.  But we're asking the victims.  Teammates who were inconvenienced, enemies of the capes in question, all of that.  Is this cape in prison worth letting free?  Knowing what's at stake, are you willing to put the past behind you and give them a second chance?''



She smirked.  ``And you're my victim?''



``Me and the Brockton Bay Wards,'' I said.  ``The Undersiders were asked, too, but they gave their votes to me, with only a few words of suggestion.''



\emph{She's fucking useless}, Imp had said.  \emph{And she shot my brother.  Bitch isn't worth having to worry about being shot in the back with a crossbow}.



``Moronic,'' she said.  ``Making it a popularity contest.''



``Doing what we have to,'' I responded.



``Moronic,'' she said, again.  I might have missed it, if it weren't for the repetition of the same word.  Slightly different.  A hint of emotion?  Disdain?  Disappointment?



Maybe she cared more about being freed than she was letting on.



Maybe, on a level, she grasped that she was reaping the consequences of earlier actions.



Well, I'd been there.



``I suppose this is the point where I'm supposed to beg?  I give you some satisfaction, you get some\ldots''



``Closure,'' I said.  ``No.  I'm not going to make you do that.''



``Because I won't,'' she said.



``I know,'' I said.



\emph{It's not in you, based on what you've said here}.  That personal pride, the security she'd apparently found in knowing what her niche was in the world and how she fit into it, it was her mask, the barrier she erected against the world.



``You hurt people,'' I said.  ``And the way you reacted to me, on that night where the Undersiders kidnapped you, trying to slash my throat\ldots you've killed.''



``Yes.  So have you.  You might have a body count higher than mine.''



``I might,'' I said.



``You hurt people too.''



``I did,'' I agreed.



``A lot more than I did.''



``Probably.''



``And you weren't even subtle about it.  Taking over a city, robbing banks, attacking the fundraiser, attacking the headquarters\ldots''



``Extorting the mayor,'' I added, ``Unlawfully imprisoning people, a lot of other stuff.''



``Yet you're out there and I'm in here,'' she said.  Then she \emph{smirked}.  ``Funny how that all works out.  It all comes down to strength in the end.  Power.  How useful are you to others?  I was useful, strong, even marketable on a niche level, and they pulled strings for me.  Pulled \emph{your }strings, even.''



``Yeah,'' I said.



``But I became more trouble than I was worth.  They throw me in jail, say it's because of a probation violation.  But why are they \emph{really} doing it?  Because I'm more trouble than I'm worth.  I'm not \emph{useful}, am I, Hebert?  Regent got me, I was a liability.  Couldn't be used to fight the bad guys.  They sacked Piggy for the same reason.''



``Even if that was true, they could have moved you to another city.  They would have,'' I said.  ``But maybe you burned bridges.  Maybe the other teams didn't want you.''



She shook her head a little, her smirk turning up a little.



``I think your view is a little narrow,'' I said.  ``It's about more than usefulness.  There are other factors.''



``Like what?  Likability?  Substance?  Respect?  Trust?''



``Along those lines,'' I said.



``Bullshit,'' she said.  Her eyes narrowed.  ``You think you're more likable than I am?  Fuck that, and I'm not just joking around like we did back at school.  You and I?  We're the same.  We're tough where we need to be, we hit hard so our enemies aren't in any shape to hit back.  We're good at what we do.  Difference is you were a little luckier, bet on the right horse.''



``No, Sophia,'' I said.



``No?  You run, right?  It was on TV.''



``I run, yes.''



``And you don't think you were trying to emulate me?  Subconsciously?  I was on the track team, and there you are, a bit of a loser, looking for a way to improve yourself, and you start \emph{running}?''



``Not even remotely close to the mark,'' I said, feeling a note of irritation.  ``Not on that count.  The other stuff?  Maybe we are similar in respects.  Maybe being a cape in this fucked up world means you have to go that route, just a little.''



``Being a person,'' she said.  ``Dealing with reality.''



``Maybe,'' I said  ``But if I \emph{was} like you, I was better at it than you were, went further, tested the limits more.''



I could see her eyes narrow further.



``And I think it's a pretty shitty way to exist,'' I finished.



``Ouch,'' she said.  ``You \emph{wounded} me.''



I couldn't hear anything in her voice, nor could I see anything in her expression\ldots but her shoulders were tenser, her hands had stopped fidgeting and were still.



I stood from my chair, collecting the phone.  I glanced at it.



NZ gutted.  Timeline for counterattack set for 1.5 hr from now.  Testing efficacy of some abilities at range.  Legend, Pretender, Eidolon on board to help.  Weaver has been requested for assistance and field administration.



``You're going, then,'' Sophia said.



``Yeah.  You said you wouldn't help, you'd rather scurry away like a cockroach.''



``I'm not saying \emph{I'd} rather.  I'm saying it's what we should \emph{all} do.''



``Either way.  You're free to convince me.''



``To beg, we're back to that.''



``To \emph{convince me}.''



She shook her head a little.  ``Fuck it.  Let the world burn.  We'll all be better off.  No pretension, no fakery, none of the tradition and `this is the way things are and always will be'.  Hit the reset button, whoever's left will pick things up later.''



``That sounds remarkably similar to how Jack sounded.''



``Fuck you, Hebert.''



``Fine.  I'm walking away from this with a clear conscience.  Sit there in your cell and worry every \emph{minute} that Scion's going to come tearing through here and wipe you off the face of the planet.''



She smirked, but I could see that tension in her neck and shoulders, still.  I felt like Rachel, looking at someone and trying to piece together their natural responses, figure them out.



Or was it the opposite?  Was I like Rachel in how she looked at a dog, understanding them on a level most people couldn't?



``You're afraid,'' I said.



``\emph{Fuck you}, Hebert,'' she spat the words.



``You're afraid and you're hiding it behind a very good mask.''



``Fuck \emph{that}.  I hate that fakery, that false-faced bullshit.''



``You said we're alike.  You're right.  We're both very good at putting on a front.''



She snarled the words.  ``There's a difference between acting and \emph{being}.  I'm not faking anything.''



``Yet you refuse to do anything to deviate from your path.  That's why you're so big on sticking to your place.  If you never budge, you never have to risk seeing if the mask comes off.''



``Oh fuck the hell off, Hebert.  You sanctimonious, know-it-all, \emph{orphan} bitch!''



She'd picked the `orphan' bit to hurt, to get a rise out of me.  Yet I felt okay.  Hurt?  Yes.  I felt something deep and important missing, and I wasn't quite ready to let myself feel that emotion in its entirety.  To hear the words in full or see the body and \emph{know} my dad was gone.



I needed to do that, and maybe to do it soon, if only to pay respect to my dad.



So yeah.  I hurt.  I felt the sting of her words.  I still felt off kilter.  But I was calm.



No act.  No mask.  \emph{Me}, and I was okay.



``Thank you, Sophia,'' I said.  ``I feel a hell of a lot better than I did before this meeting.  I don't know if-''



``Loser.''



She'd gotten the guard's attention with her outburst.  The woman was approaching.



``-if you were right about us being similar or not.  But I don't want to be the sort of person you could compare yourself to.  I'm going to be Taylor again, so thank you, for helping me come to peace with that.''



\emph{I can be Taylor without being weak}.  \emph{Keep the best parts of Skitter and Weaver.}



I turned to leave.



``Fuck you!''



Her maneuver was a practiced one, no doubt something she'd trained herself with in her cell or in the moments she was cuffed and unobserved.  A way to buy herself a fraction of a second to use her power, where her wrists wouldn't come in contact with the cuffs, as she let them drop from a point further up her arms to her hands.  I could sense the motion with my bugs.



Her leg hooked under her chair as she made it as shadowy as she was, and she kicked out, sending the chair flying through the bulletproof glass.  It rematerialized as it crashed into mine, and the two chairs in turn hit me.



I stumbled.  My shin stung where the little folding chairs had hit me.



Sophia, in turn, was being held down by the guard, the handcuffs pulled taut against her wrists.



``Is this the real you, then?'' I asked.



``Oh my god, you pre\ldots pre-''



``Pretentious.''



``\emph{Cunt!}''  Sophia snarled the words between her grunts of struggle.  ``I'm going to \emph{break} you!''



``Take a minute or two to calm down,'' I said.  ``Breathe.  If you can relax, if you can look me in the eye and promise you won't hurt me or anyone else, I'm going to give the go-ahead for you to leave.''



There was a pause, shock stopping both the guard and Sophia.



``You're joking,'' the guard said.



Sophia just lay there, her head pressed against the little ledge, panting.  Her hair covered her face.



``Offer's open just a bit longer, Sophia,'' I said.  ``I want to take some time to get ready, and if you're coming, you'll need the same.''



She didn't budge.  The guard took her weight off Sophia, and only held the chain of the cuffs, twisting so Sophia's arms were held taut above her.  It must have been uncomfortable with the way her body was forced to one side, her head forced down.



\emph{Afraid}.



``I'm not asking you to fight Scion.  Just doing search and rescue would be fine.  It's not \emph{safe}, but-''



``Will you\emph{ shut up}?''  Sophia's voice was muffled, not in a position to let her voice pass through the perforated space in the glass.  ``Fuck, I'll do it if you stop \emph{prattling} at me.''



``Look me in the eye and promise you won't fuck with me.''



The guard let Sophia straighten.



She met my eyes, glaring as if a look alone could express a hundred different kinds of violence.  ``I promise.''



I shrugged.  The guard looked at me, and I nodded.



``Your funeral,'' she said.  ``I'll go take her to the back and get her ready.''



``No need,'' I said.  I looked towards the ceiling.  \emph{Let's try this}.  ``Two doors, one for me, one for her, to where the others are on Earth Bet.''



The doors opened, rectangular windows.  Unlike the portals I'd seen before, these ones were dark, one on each side of the bulletproof glass.



Sophia, still cuffed, shot me an ugly sidelong glance, watching as I made my way through the portal.  The door was already closing as I saw her turn and step through the other.



I didn't want to let her loose without any observation.  I'd bring her along for just a short while, then find a place to stick her.



I felt okay with this decision.  Comfortable.  It wasn't a mask I was wearing, so strong it might as well have been real.  No.  It was something simpler.



\emph{I'm not scared of her anymore.}



\sectionbreak



There were other, bigger things to be scared of.



The sky was overcast, but it wasn't wholly clouds.  Dust choked \emph{everything,} thick and heavy.  The sun was rising, and it felt like it had been rising for some time.  The issues of teleporting across time zones.



Red.  The sky was a surprising red color, filtering between clouds that were almost black.  It cast the tall mountains in similar shades, with deep shadows and vivid color.



My breath fogged in the air.  I'd been dressed for summer.  This\ldots it was cold.  The landscape around us looked like coals resting in a fire, cast in ash white, charcoal blacks and reds, but it was \emph{cold}.  The cold leeched warmth from my feet, even.  We were on a mountainside, a broad, flat ledge that could have held three helicopters.  Instead, it held one Azazel suit and a crowd of perhaps sixty.



The cold wasn't just the altitude.  The levels of dust in the atmosphere would be having an effect as well.



My bugs were having a tough time here.  I clustered them against my body, more so they could benefit from my warmth than the opposite.



With the bugs so close to me, crawling on my skin, in the cradle of my folded arms, and beneath my clothes, my sense of others was limited.  Even so, I could sense Rachel's approach.  I didn't react as she set her coat over my shoulders, except to glance at her and nod my thanks.



A crowd had gathered.  Everyone from the meeting, minus Saint, was present.  There were also innumerable others who hadn't been at the meeting.  Some I recognized, many I didn't.  Here and there, portals opened and people stepped through, joining the crowd.



``Long time,'' I heard someone say.  Boston accent.



I turned around.  It was Weld, with his partner, the tendril-girl that wound around his body.  He hadn't been talking to me.



No, his focus was on Sophia.



``Hey chief,'' she said.



He gripped the two loops of her cuffs, and absorbed them into his hands.  She rolled her shoulders, then rubbed at her wrists.



``Don't cause trouble,'' Weld said.  ``Too many people on edge here.''



``Yeah,'' Sophia said.



Then Weld left, returning to his group.



Sophia was left standing there alone, cold in her prison sweats.



Time passed.  I'd hardly arrived in the nick of time, for the main event.  I walked around the edge of the ridge, navigating around clusters of people, then approached the Azazel.



Tattletale was within, her attention on the computer screens.  Defiant was leaning over her, giving instructions.



I left them alone, joining Rachel and Imp, where they sat with their backs to Bastard's side, feet inches from a precipitous drop.  Grue was keeping more of a distance, simultaneously watching and keeping as far away from Bonesaw as he could manage.



``No more malls,'' Imp was saying.  ``No more going \emph{shopping}, no more reality TV, no more stupid boy bands to make fun of\ldots''



``What are you doing?'' I asked.



``Talking about everything I'm going to miss,'' Imp said.  ``I'm trying to start from the outer edges and work my way in towards the biggest stuff.  Work up my courage to say, you know\ldots''



``You'll miss \emph{us}?'' I asked.



``Aw, you're so full of yourself!''  Imp said.  ``It's so sweet!  I was going to say, um, those creepy little kids who look way too much like their big brother?  I'll miss them way more than I should.  I'd miss them more than I'd miss you.''



I reached over and pushed her head a little, trying to mess up her hair and failing to do so before she'd pulled away.  I found a seat beside Rachel.



Bastard's chest rose and fell.  It was one element of an uncomfortable seat.  Warm, but not quite cozy enough for me to nod off.  It was too cold, for one thing, and I felt my rear end going numb from the cold before I'd been sitting for a minute.  Even more alarming was the general sensation that someone was gently pushing me towards the ledge, then easing up, pushing me, easing up.



If he lurched to his feet for any reason, I wasn't entirely sure I would be able to stop myself from being shoved over the precipice.  \emph{I should have worn my flight pack.}



``I don't have a lot,'' Rachel said, breaking the silence.  ``Haven't ever had much more than I could take with me if I left home.  Had money, but it was just a number I couldn't really follow on a computer I didn't have.''



``You have something now,'' I said.



She bobbed her head in a motion that was almost too slow to be a nod.  ``Yep.''



I didn't elaborate.  We watched the crimson sunrise.



``Don't want to lose it,'' Rachel said.  ``Any of it.''



\emph{I-}



I couldn't even complete a thought, hearing that.  \emph{Damn it, Rachel, }\emph{don't say that, don't remind me}.



I thought of my dad.



Of my mom, though that was a wound I'd thought I'd healed.



I thought of my hometown, which wasn't quite home anymore.



I thought of my pride, my \emph{mission}, neither of which I quite had anymore.



I lowered my head, bringing my knees up to support my arm as I nestled my face into the crook of my elbow, burying it into the fabric of Rachel's jacket.  This was too public.  The wolf's overlong body provided a barrier between us and everyone else, but\ldots too public.



``Sorry,'' I mumbled.  My tears were hot against my face.



``Why the fuck are you sorry?'' Imp asked.



I raised my head up just a little, trying to pull myself together.  ``Feeling kind of- my feelings are all over the place.  A little unhinged.''



Imp didn't look my way, instead turning the narrow black lenses of her mask skyward.  ``It's been a bad day, in case you haven't noticed.  You're \emph{allowed} to feel bad.  It's kind of normal.''



Normal.



I'd been thinking of my feelings as being off-kilter, out of control, unreasonable and irrational.



Were they just regular feelings?  Emotions that weren't being reined in by my discipline and bottling everything up, by distraction and disconnection?



Somewhere along the line, I'd stopped thinking about my feelings as being mixed up or fucked up and stopped concerning myself with them altogether.  On a level, I'd blamed my passenger.



But I wasn't sure I could justify that with what I was experiencing now.  Why would the passenger take away, gain ground in subsuming my identity and then give it back, all like this?



Was it just me?



\emph{Fuck. } I wasn't sure I wanted this to be me and me alone.



I lowered my face into my elbow again.



Why?



What was it all for?



I drew in a breath, trying to keep my breathing level so I wouldn't give any \emph{audible} clues as to what was going on, and it backfired.  My breath hitched and I released a little hiccup of a sob.  It was all downhill from there.



I didn't care anymore.  I wasn't about to mentally berate people for caring about secret identities when we were so far past that, and then care about my reputation or how I looked.



Screw it.  If I was going to be \emph{Taylor} again, I wouldn't give a fuck.



Rachel put her arms around my shoulders in a clumsy hug that squished my shoulder.  Then, with the hand of that same arm, she reached up and put her hand on my head, rubbing left to right and back again.  My head rocked with the motion.



Soothing, but\ldots ridiculous enough that I let out a little half-sob, half-laugh.



Which was probably even better than anything else.



I let my head settle against her shoulder, and she left her hand on my head, no longer rubbing.



We watched as the sunrise continued, the red of the atmosphere leaking through the gaps in the clouds.



I felt the tears stop at one point, and rubbed them away.  I had to try twice before I could voice a question.  ``How's Grue doing?''



``Ask him,'' Imp said.



I shook my head.



``He's okay.  Cozen made it out okay, but Rook didn't.  So Cozen's getting a promotion.''



``To leader?''



Imp nodded.



``Ah.''



\emph{Is there even anything to lead?  How do you manage a group of thieves when everything that's worth stealing is slowly being erased from the planet's surface?}



I wouldn't push it.



``I'm-'' Imp started.



``Ready,'' someone in the crowd called out, interrupting her.



Every single person on the broad, flat ledge of the mountainside turned.



I wiped at my face again with my hands, then stood, a little alarmed at how the stiffness of the cold hampered my movements, and the nearby ledge that yawned before us.



But no, no disasters.  We made our way around Bastard's sleeping form and joined the group.



The first of the portals opened.



A broad-shouldered man with facial hair like that of a homeless man's stepped through.  He wore prison sweats with the words `Baumann Parahuman Containment Center' across the shoulders.



``Is this safe?''  Someone asked.  A girl, in her early teens.



``They sent everyone to their cells.  Maybe a speedster could slip through, if they knew what was happening, but we have a lot of people here,'' a man next to her said.



``You didn't answer the question,'' Imp said.  ``No, it's not safe.  These guys are \emph{assholes}.''



The man with the beard turned to glare our way, inexplicably, looked momentarily confused, and then walked forward.  The crowd parted to let him through as he approached the edge.



I'd done my reading on these guys while making my way to Sophia, waiting for her to arrive.  If this went balls-up, we'd be stuck between these guys and Scion.  I'd wanted to know.



The man with the beard was Gavel.  Cell block leader.  A vigilante who had gone after families, particularly spouses and children, all so he could break his enemies before his namesake weapon could.  He'd been notorious in the days before the three strike rule or even the \emph{code}.  Even with that, people had lost patience with his `mission' when a villain had threatened to detonate a small bomb, and Gavel had called a bluff that wasn't a bluff.  Gavel had walked away.  Many, many others hadn't.



A woman ventured forth.  Her hair was long, her features matronly.  She wore a prison uniform that had been cut apart and pieced together into heavier cargo pants and a jacket.  Lustrum.  Part-celebrity, part-antihero, she'd gathered a following of college-aged feminists, building up an almost religious fervor, before giving the fateful orders that turned things violent, pushing her thousands of followers to humiliate men, often violently.  Things soon escalated to the point that more fanatical followers were emasculating and murdering men, even carving up followers who weren't playing along.



My mom had, in her graduate school days, been a part of one of Lustrum's groups.  She'd backed out around the time things turned violent.  I'd heard her wonder out loud, to Lacey, my dad's coworker, whether Lustrum had intended for things to get as bad as they had.



But they had.  A \emph{lot} of people had suffered.



Weird to think about, that my mom had been in the midst of this, and here we were, the loop closing.



A woman, thin, with her hair cut short, with swooping, platinum-blond `feathering' at the sides, to the point that I couldn't tell if it was just messy or styled that way.  Her eyes were the sort that looked like they were usually half closed, her features pointed.   She moved with a strange kind of fluidity, as if she had twice the usual number of joints, limbs like spaghetti noodles.  They weren't.  It was Crane The Harmonious.  Crane for short.



The records of her arrest were spotty, suggesting things had been redacted or hidden, no doubt to protect her `children' that had gone on to careers in the Wards or Protectorate.  She'd collected children with powers and raised them to be her soldiers.



She walked into the crowd, and came face to face with a hero, twenty or so years old, wearing a robe.



She stood on the very tips of her toes to raise herself up enough to kiss him on the forehead.  The kiss was prolonged to a point that it went \emph{past} weird.  The next portal was already opening by the time she lowered herself and stood with her back to her old subject's chest.



Acidbath.  Copkiller and capekiller, he'd used his power to horrifically scar innumerable opponents and girlfriends.  His blond hair wasn't the grass-green of his mugshots anymore, and he had circles under his eyes.  He took one step away from the portal, then sat on the ledge in front of the crowd, searching for something, then settling into a stare when he found it.



I looked, and I saw a man, not in costume but in a suit, standing and staring at Acidbath, with an expression as though he was going to cry at any moment.  But he didn't avert his eyes.



String Theory and Lab Rat stepped out of the same portal.  String Theory was short, shorter with her slouch, and petite, her dark hair tied back into a braid, her lips pulled back into a wide expression halfway between a grin and a smile.  With her glasses, it made me think of a frog, or a small lizard.  Lab Rat was the opposite, the last person one might expect to be a tinker.  He had a mouth full of teeth that were \emph{screaming} for braces, all crammed towards the very front of his mouth, overlapping and sticking out of lower gums.  He had a mop of hair and heavy brows, was tall and broad shouldered, and had a bit of a belly.



String Theory had made her tinker devices and then auctioned away `safeties'.  Not uses of the weapon or offering targets, but only guarantees that the owner of a `safety' wouldn't be one of her randomly selected targets.  The targets had ranged from gas stations in Indonesia to a filled football stadium in Cardiff.



As one could imagine, there had been a \emph{high} demand for her arrest.



Lab Rat, conversely, had worked in secret, developing formulas that could transform people into monsters.  He had used formulas on the homeless, then when the local homeless ran out, started picking off individuals that were isolated, out for jogs in the early morning or new visitors to his town.  It wasn't clear just what he was searching for, in developing the formulas\emph{.  }What \emph{I} found myself wondering was whether he'd been testing his work on his test subjects before using them on himself, or if it was the other way around.



Both ideas were weird, almost inexplicable.



Galvanate appeared.  He'd been one of a number of players that had supplanted the local organized crime in the early-to-mid-nineties.  A mafia enforcer with powers who had decided he had what it took to be a boss.  He'd done well, rendering entire squads of his soldiers effectively invincible, simultaneously capable of electrocuting someone to death with a touch.



Nothing short of Alexandria or an Endbringer would stand up to Scion's sustained laser beam for even a heartbeat, but there was hope that Galvanate would render some people capable of surviving a glancing blow.



Black Kaze.  A Japanese urban legend that had turned out to be too real.  Word was she'd snapped after Kyushu was destroyed.  Except she'd remained lucid throughout trials, calm, patient.  Nobody knew her real body count, but conservative estimates put it in the tens of thousands.  She'd roamed the remains of the landscape, killing survivors, killing rescuers, boarding the ships that approached too close to the ruined area and killing the crews, and rendering a widespread area devoid of life.



And with that reputation, she was only an exceedingly \emph{ordinary} looking Japanese woman in prison sweats, her hair tied back into a ponytail.  The fingers of her right hand clutched and grasped as if she expected to find something there, missed, and then reached again.



They'd \emph{apparently} talked to her and considered her okay to go out and interact with the world at large.



I watched as Masamune stepped away from Defiant and the Guild members to approach Black Kaze.



They stood there for a moment, inside each other's personal space, still but for the reflexive opening and closing of Black Kaze's hand.



Masamune returned to the cluster of Guild, and Black Kaze followed, directly behind him, head bowed a little.



Ingenue, not quite the pixie I'd seen in her mug shot, eight years later.  She'd been wide-eyed and \emph{cute} before.  Now she was an attractive woman, but not quite someone who could have starred as the girl next door in a teen movie.



Hopefully she had changed in her habits, as well.  She'd partnered herself with three male capes, heroes.  \emph{They }had gone to the Birdcage, and records suggested they hadn't survived more than a day after her return.  When the \emph{fourth} partner had used his power to poison a town's water supply, killing nearly a thousand people, people started wondering about the common denominator – the girlfriend.  The fourth had gone to therapy, and Ingenue had made her way to the Birdcage.



She extended a hand, pointing a painted nail, and swept her hand over the crowd.  She settled on her target.



Her walk was a practiced one, with a swaying of the hips, an unhurried pace.  She approached Chevalier, then wrapped her arms around him, raising one leg off the ground.  Chevalier, for his part, didn't move a muscle.



Marquis was next to arrive.  His brown hair and beard were just now starting to get strands of gray in them, wrinkles at the corners of his eyes.



He'd been one of the scary bastards of Brockton Bay well before the Undersiders were even on the map.  A guy who could go toe to toe with a full squad of Empire Eighty-Eight and walk away.   He'd been successful enough to pay for hirelings and ruthless enough to execute them for failures.  His path to the Birdcage had been very similar to the path that had almost taken me there; so many violations of the law that the three strikes rule had been left \emph{well} behind him by the time the good guys finally won.



He didn't look quite so intense as his mug shot.  He seemed calmer.



Even sorrowful.



He approached the crowd, and he stopped in front of a woman I recognized but couldn't place.



In the moment she slapped him, I drew the connection.



Lady Photon.  Sarah Pelham.



Flashbang and Brandish were with her, looking just as grim.



All around them, people were tensed for a fight.



That stopped when Marquis nodded solemnly.  He murmured a few words, then walked away, standing on the same ledge that Acidbath had perched on, a little to the right of Lab Rat and String Theory.



Teacher emerged, and I searched the crowd for Saint.



Absent.



Teacher was a mundane looking man.  If one were to put a argyle sweater and khakis on him and put him in a classroom, he would have looked well at home.  He had a receding hairline, with curly hair that had been cut short-ish.



Crimes: conspiracy to assassinate the Vice President of the United States.  Successful.  Conspiracy to assassinate the Prime Minister of England.  Successful.  He picked big targets, took his time and was \emph{successful.}  Setting up his pawns and giving them the low level thinker powers they needed for observation and information gathering, for getting glimpses of the future or intuitively knowing how to hack or decrypt, or for knowing the weaknesses of their enemies and how best to hurt them.



Followers that remained absolutely loyal as long as they had the granted powers.



Saint had wanted him more than he had wanted to retain his control over Dragon's power.  \emph{Why}?



Because having Teacher free would give Saint the capacity to regain control of that power \emph{and }to use it at its full capacity?



It didn't matter.  We'd win this first and then we'd deal with that.  Whatever Teacher was capable of, it couldn't be worse than Scion.



In a manner typical for royalty, Glaistig Uaine was fashionably late.  The Faerie Queen.



Just like String Theory's terror campaign had driven people to desperation in their attempts to stop her from her scheduled sprees of destruction, Glaistig Uaine had drawn entire \emph{flocks} of capes down on her head, by virtue of her habit of finding, killing and claiming the `spirits' of capes.



Thing was, they'd sent multiple teams after her, and they'd \emph{failed}.  Thirty two capes killed and claimed.



So they sent more after her.  Again, they failed.  Of the fifty who were forced into a retreat, thirteen were killed and claimed.



When that wasn't enough, they hit her with \emph{everything}, only for her to surrender.



She walked into the Birdcage of her own will.



Now they'd let her out.



The cell block leaders.  They'd held their own, maintained their territories, and had been okayed to stick around by the thinkers.  That double-check didn't have as much weight as it should have, given how this one group alone had no less than three ways to screw with thinkers.



But they were firepower.



We had roughly forty-five minutes to half an hour before we'd take our first shot at Scion.  Try as much as we could while risking as little as possible.  These guys would be assets at best.  Cannon fodder at worst.



Other prisoners were arriving.  Dozens.  Some seemed to be subordinate to the cell block leaders.  Others, they didn't look like they had a place to go.  I watched Lustrum beckon to a girl with yellow feathers in her hair, and the girl didn't budge.



I saw Lung step forth, in the company of several capes.  He stopped, taking in a deep breath, then exhaled with a volume I could hear.  He was shirtless, and didn't move to cover himself up, even with the cold.  His eyes roved over the crowd, and settled momentarily on me, on Rachel, and Grue.



Then Panacea stepped out.



She was different, her wild brown curls tied back into a plait, her face thinner, with more pronounced cheekbones.  She wore a camisole, with her prison jacket tied around her waist.  Tattoos marked the length of her arms.  A sun held a position of prominence on her right arm, a heart with a sword on the left.



The simple tattoos, symbols and ideas got denser as they got closer to her hands, and a vibrant red ink marked the space between the individual black and white images.



\emph{Blood on her hands}.



I was \emph{very }aware of how the common prisoners around her stepped away when she stepped forward.



Very aware of how Lung spoke to her, \emph{casually}, his voice a low bass rumble as she scanned the crowd.  Her eyes locked onto the members of New Wave.  Her mom and dad.



Brandish advanced, wrapping her arms around Panacea.



Panacea received the hug in a stiff way.  Her eyes were downcast.



As if to distract herself, she raised her eyes, scanning the crowd.  Her eyes fixed on me, on Rachel, Grue and Imp.



I saw a momentary look of puzzlement cross her face as she looked at Sophia standing off to one side, then back to me.



She mouthed a word.  I didn't hear it over the murmurs of the crowd, the discussions.



\emph{What}?



Then her eyes fell on someone else.  On Bonesaw.



Bonesaw raised her hand in a short wave.



\emph{This} time I heard Panacea.



``\emph{Fuck me}.''





