





The last portal closed.  The Birdcage had been emptied of everyone that could reasonably be let free, and probably a handful that shouldn't.



We'd deal with that later.



``No faces present that shouldn't be?''  Chevalier asked.  Ingenue was standing beside him.



``Every person on the list has a corresponding face in the crowd,'' Defiant said, ``Going by the facial recognition program.''



Chevalier nodded.  ``With respect, I'd like to ask everyone who isn't participating in the upcoming confrontation to please leave.  The others, your enemies, your teammates, friends or family, they need to focus on stopping Scion.''



Crowds had body language and attitudes much as individuals did.  Though they were mingled with the capes in the area, the people who'd arrived to see the people leaving the Birdcage were easy to pick out.  They shifted position, as if Chevalier's request had a physical force to it, a wind pushing at them.  Then they planted their heels.  Hesitation, out of love or out of hatred.



But the portals opened, leading to different worlds.



``Bet, New York!''  someone announced, as a portal opened.  ``Bet, Red Fist HQ!  Gimel, New Brockton settlement!''



More portals opened as locations were announced.



The bystanders began filing away as their destinations were called out.  I was surprised to see New Wave among them.  Brandish said something to Panacea, squeezed her hand, and then turned to leave.



Had they retired?  Given up on fighting?  Or was this simply a fight on a scale they weren't prepared or able to participate in?



``I'm going to go,'' Rachel said.



``Yep,'' Imp said.  ``No use for us here.''



I looked at them.



``Okay,'' I said.



``Me as well,'' Grue said.  ``Cozen-''



``No,'' I said.



He stopped, tilting his head at a funny angle, as if he could get a better understanding of me by viewing me from a skewed perspective.



``You're not useless.  I get if you don't have the courage, but your power, there's potential.  Even if it doesn't work, that tells us a lot.''



He folded his arms.  ``If you say so.''



I nodded.



``Okay,'' he said.



He stepped back as Rachel and Imp made their way to Gimel.



Parian and Foil hugged, and then Parian passed through, leaving Foil behind.



Sophia turned to go as well, very casually avoiding eye contact with me.  She didn't want me to raise an issue, so she was slinking away.



I drew bugs from the other side of the portal together, then whispered a message to her.  ``\emph{I'll talk to you later}.''



She turned, but the people behind her were pushing forward.  She couldn't exactly turn back to retort.



The portals closed.



``Forty-five minutes,'' Chevalier announced.  ``We've got Defiant and Tattletale at systems, managing Dragon's A.I. and running the data.  \emph{They} are your resource, the people you go to if you need something, be it information or materials.''



I glanced at the Azazel.  Tattletale was sitting on the ramp, while Defiant stood at the end, near Chevalier.  Tattletale would process the data, picking up the essential details, while Defiant would handle the lion's share of the code.



``They should be able to accommodate all requests, so don't be shy.  Keep them updated on \emph{everything, }the plans, the weapons, the possible applications of your powers.  They'll categorize and prioritize your plans and we'll relay that information to people with the ability to put that into a plan.''



\emph{To Cauldron}, I thought.



``Forty five minutes isn't a very long time,'' Lab Rat commented.  His voice was a rasp.



``No.  But Defiant has been mapping Scion's route with his analysis engines, and Scion \emph{is} somewhat predictable.  He's spent the last few hours veering between extremes, choosing different kinds of targets.  He strikes a major population center, then scales down to strike a \emph{select} target.  Individuals, a subcategory of the population like adults or capes, or properties.  Right now he's in one of those lulls.  We expect that, in forty-five minutes, he'll move on to a bigger target again.  With luck, this attack will serve to distract him and buy us time to finish evacuating.''



``He's tough,'' Defiant said.  ``You know that.  He took on Behemoth with minimal effort.  This is an attempt to see if we can find his limit, any weak spot, weapons that work.  If we can, we expand, extrapolate.  Keep that in mind and prepare accordingly.''



``Alright!  Let's move!'' Chevalier announced.  ``First up, a door to the New York sub-office!''



The portal began to open.  Chevalier continued, ``If you don't have access to costumes or weapons, we'll outfit you here.  Defiant and Tattletale will direct you to other locations for other goods.''



I watched as a bulk of the forces began to head through the gate to the New York location.  Chevalier and Revel stood by the portal, watching the various capes as they made their way through.



I, too, hung back, watching.  I could get a fresh costume and a spare flight pack easily enough.  I wanted to know what the others were doing.  The people who were hanging back.



Slouching, hands clasped behind her back, String Theory made her way over to Chevalier and Defiant.  The petite, odd-looking woman glanced around, not speaking up, but waiting until Chevalier deigned to look at her.  Lab Rat, behind her, looked more impatient.  He wasn't good at hiding his feelings.



``I'll need a lab,'' String Theory said.  ``Tools.  \emph{My} tools, if you can get them.''



``You can prep something in time?''  Chevalier asked.  He sounded surprised.  ``We expected the tinkers to take part in the next attempt.''



``I'm not an ordinary tinker,'' String Theory said.  She tapped her head.  ``I've had four years to think, plan what I'd build if I got out.  All up here.''



``Me too, seven years of thinking,'' Lab Rat said.  ``Need a lab.  Not sharing one with \emph{her}.''



``I wouldn't let you, darling,'' String Theory said, condescending.  I could see Lab Rat's lip curl, but I wasn't sure if it was in irritation or amusement.



``You'll both have what you need,'' Chevalier cut in, before anything could start between the pair.



``Tell me what you need and when,'' String Theory said.  ``You want me to hit him?  Tell me how hard.''



Chevalier glanced at Revel and Defiant.



``When you were arrested,'' Defiant said, ``The-''



``The F-Driver,'' String Theory interrupted.



``Yes.  Start from there, scale \emph{up}.''



``Oh,'' String Theory said.  ``Interesting.''



``With a minimum of collateral damage,'' Defiant added.



``Less interesting.  Next question\emph{: when}?  My work is one-shot, and my best work is on a timer.''



``We attack in\ldots thirty-nine minutes.  Time things for forty seven minutes from now.  Most of the combatants will be cleared from the field by then, and the rest can move to safety before you put your work to use.''



String Theory nodded slowly, ``You'll hold out for eight minutes after the initial offense?''



Defiant paused.  ``Make it forty-three minutes from now.''



``Done.  I'll need a fusion reactor.  Or a suitably large source of plasma.  Something I can draw power from.''



``We don't have-'' Defiant started.  Then he reconsidered.  ``We may be able to find something from tinker materials the PRT has confiscated.  Go inside the ship, talk to Tattletale.''



Without another word, String Theory turned to advance up the ramp, disappearing inside.



Defiant looked at Lab Rat.  ``Your old workshop is still there, sealed off.''



``No.  I'd be spending more time cleaning up than working, and the samples would be dead, if you haven't tampered with them.  Something else.  A room in a hospital would work.  I can stay out of the way.''



``We're not giving you access to humans,'' Defiant answered, his voice hard.



Lab Rat frowned.  ``Animal shelter?  With the animals still present?''



``Fine,'' Defiant said.  ``Thirty-seven minutes.  If you're going to contribute, you should get started.  Door, please.  To an abandoned animal shelter on Bet.''



The door opened.



``Mm,'' Lab Rat grunted.  ``I'll figure something out.''



Then he was gone.



``And me?'' Bonesaw asked.  ``I can help.''



``You will help,'' Defiant said.  ``After.  When you work, it's going to be with supervision.  Panacea can check your work and vice-versa.''



Bonesaw sighed.  ``My lab.  The alternate dimension, the cloning vats-''



``Destroyed,'' Defiant said.



``You're serious?''



He didn't respond.



Bonesaw scowled.



I shivered and looked out at those who remained.  Panacea hadn't gone with the other members of New Wave.  Instead, she sat on the cliffside with Marquis.



I felt a stab of something ugly, seeing that.  I couldn't justify or explain it, let alone give it a name.  It felt fundamentally \emph{unfair}, and I couldn't rationalize it.  Life wasn't fair.  Good guys sometimes got the breaks and sometimes they didn't.  \emph{Bad guys} sometimes got the breaks and sometimes they didn't.  Panacea had taken more bad hits than most, and yet I wasn't able to convince myself she deserved to have that.



Not because she \emph{didn't} deserve the chance to sit and stare at the view on this cold mountainside with her father beside her, but because an irrational part of me wanted to have it instead.



Someone to sit beside, to talk with, to discuss things, to be \emph{able} to talk about stuff without avoiding everything cape related\ldots someone to lean on, who'd been through some of this stuff.



I turned away.



Acidbath had stayed, rather than leave to go get a costume, and was splayed out on the rock of the cliff face, his shirt off and laid out beneath him.  Soaking up the rays, insofar as they was any sun to be had.



Just a short distance away, Glaistig Uaine was using her power.  A shadowy figure, translucent, was kneeling before her, hands raised in a supplicating gesture.  The figure had created a flame in the two joined palms of its hand, and Glaistig Uaine was using the flame to warm her hands.



I hesitated a moment, and then approached her.



``Queen administrator.''



``Faerie Queen,'' I responded.  ``Mind if I share your fire?''



``Not at all.''



I glanced down at the spirit.  It wasn't smoky or blurry, and was fairly substantial, all things considered, but the features of the costume that the figure had once worn had been smoothed over, to the point that the line between costume and flesh was impossible to discern.  An overly pointed nose, sweeping up into flames at the sides and top of the head, eyes without irises or pupils, pointed fingertips with more flames at the edges of the wrists.  The gender indeterminate.



Odd, that it had picked up on something so integral as costume, but not identity.



How had Golem put it?  Someone who'd had a life, a mother, a father, family.  He'd had dreams, had undergone a trigger event or paid a small fortune for powers in a jar.  He'd had a story.



Relegated to being a servile handwarmer.



Was there any of the original personality in there?  The memories of the person that was?  If there were, then it implied something ugly.  Glaistig Uaine collected passengers, tapped them for power, and if this thing had memories, then what did that suggest about the passengers?



I didn't want to be cold and uncaring anymore, I didn't want to be calculating and efficient.  It made \emph{sense} to ignore this individual, the spirit, to maintain peace with the Faerie Queen, but I didn't like what it forced me to do.



So, instead, I turned to the spirit.  ``Hello.''



It opened its mouth to speak, but the words were faint, incoherent, as though it were emulating language rather than actually uttering it.



``Did you have a name?''



``Phoenixfeather,'' Glaistig Uaine said.



Bit of a mouthful.



I warmed my hands at the fire.  ``Thank you, Phoenixfeather.''



He only lowered his head, shutting those featureless eyes that could have been lenses.



I felt a bit of a chill at that.



What if I fell in battle?  Would she claim me?  Would I become like \emph{that}?  What form would that body take?  Skitter, Weaver, or a blending of the two?



``You're not armed for battle,'' the Faerie Queen observed, as if reading my mind.



``No.  Soon.''



``Yes.  I wait as well.  The head that wears the crown bears a heavy burden.''



``You view us both as queens, Faerie Queen?''



``I do.  But let us drop the titles when we talk.''



``Okay\ldots Glaistig Uaine.  Anyone else?''



``There are others who stand shoulder to shoulder with us, but queen is the wrong word, Administrator.  The champion, the high priest, the observer, the shaper, the demesnes-keeper.  Why do you ask?''



``Just trying to make sense of it, trying to figure out where \emph{you} stand.''



``Ah.  Do explain.''



``You want to see the faerie rise again, apparently, and Scion's a big part of that whole equation.''



``Yes.  I'm seeing what you're getting at, Administrator.  A conflict of interest?''



``Essentially.''



``We all have our parts to play.''



``Parts.''



``Yes.  Like actors taking a role in a play.  We wear our human faces and harbor our dramas and fantasies, but it's the same individuals playing the parts, as the play starts anew on a different stage, with different faces and forms.  If it all goes well, a figure from the crowd joins the stage for the plays that follow, and the roles are refined.''



``And us\ldots Queens and Kings.  Do we have a bigger part?  Leading roles?''



``Everyone's the lead in their own story, Administrator.  Some roles are bigger, some smaller, but none are more \emph{important, }understand?''



``Yes,'' I answered her.  ``What's your role in this, then?''



``We're back to the topic of my\ldots conflict of interest.  I have a special role in this.  I keep the company of the faerie who have left our metaphorical stage.''



``The dead,'' I said.  ``You keep the company of the dead.''



``Yes.  The other nobles, their tasks are more immediate, shorter in term.  What makes us truly \emph{noble} is our role before and after this act.  The others sleep, and we toil.  We're practiced, stronger, for that constant effort.  The champion and observer ensure the next act goes on without a hitch.  The shaper and demesnes-keeper clean up after we are all done here, one way or another.  So it goes.''



``And the priest?''



``The \emph{high} priest,'' Glaistig Uaine admonished me.  ``You and I may be doing without the titles, but we mustn't offend the others.''



``Right,'' I said.



``As for his role, well, you should know.''



``I should know?''



``Yes.''



I could only think of one powerful individual who was on a par with the others she'd named.  Contessa and Glaistig Uaine were easily twelves or higher on the power-ratings scale, and I could look to others with powers in that neighborhood to figure out who she was referring to.  Panacea, Labyrinth\ldots



Which raised two questions.



Why the hell was I on that list, for one thing?



And was Eidolon the high priest?  He was the only one I could think of to fit the role.



``I'm not sure I follow,'' I said.



``He doesn't follow either,'' Glaistig Uaine replied.  ``Which complicates things.  We have two courts, but the other court arrived to the stage bedraggled, maddened, and they don't have any instructions or forewarning, you understand?''



``I believe so,'' I said.



\emph{Trying to, anyways.}



``The high priest is in similar straits to these unfortunates.  He stands straight and bluffs through his lines, but he's wearing the wrong costume and he's arrived at the wrong time, just like the others.''



``And\ldots what does \emph{he} think of this?''



Glaistig Uaine shrugged.  ``I couldn't tell you.  But what would you think of it, in his shoes?  He's set this in motion, and there's no finale, there's no promise of another play after this one is done.  The nobles of our court's mighty faerie may have no role to play.''



``But you're not concerned?''



She smiled a little, but didn't respond.



``If it comes down to it, if we \emph{somehow }get one over on Scion and if it looks like we might win, are you going to back him up?  Because you want to see the next play?''



She used long fingernails to tuck hair behind her ear, turning pale eyes towards the horizon.  The sky was still red, but it was more to do with the dust-heavy atmosphere than the sunrise.  ``I do wish to see it.  I'd like to see the spirits of the dead dance through the landscape, even more than they are right now.  Yet I'm still carrying out my role, and that's the evidence I'll give to my loyalty in the here and now.''



I wasn't quite putting two and two together, and I suspected that might have been because she didn't want me to.  She was still carrying out her role, which was to collect and comfort the dead.  Because\ldots she hoped this all to go according to Scion's plan?



I looked down at the fire that her shadowy specter was creating, then to the specter.  To Phoenixfeather.



I'd watch Glaistig Uaine for trouble.  I thought of the other major players who I already was keeping mental tabs on.



``What is Scion to you?  He's the director of this\ldots play?''



``The audience, as well.  The metaphor falls apart at this.  He's our father, our child, our creator and now our destroyer.''



I could grasp that much.  Was there another I could ask about, that I wasn't so sure about?



``Doctor Mother,'' I said, without even really thinking about it.  ``Can I ask what role she plays on this stage?''



``Ah, now you're asking me to answer questions that could make enemies.''  Glaistig Uaine glanced up at me, and there was an implicit threat in the glance.



``I wouldn't ask you to answer questions if it was inconvenient, Glaistig Uaine.  I'm sorry.''  \emph{Be polite, keep in her good books}.



``I should hope you wouldn't,'' she said, and there was an admonishment in her tone.  Then, her tone lighter, she replied.  ``No matter.  She's not one of ours.  A prop, nothing more.''



``No powers, then.''



``Like I said, a prop.''



``She doesn't seem that unimportant,'' I said.  ``She has a lot of power.''



``A prop can be important.  The grail was a subject for innumerable quests and tales.  A message can decide the outcome of a war.  A \emph{living }prop\ldots''  she trailed off.



``Forgive me, Faerie Queen,'' I said.  I saw her start to object, then hurried to continue, ``I'm using your title because I'm about to be rude, and I do want to show you the respect you're due.  It's been a hard day.  I'm not quite so distanced from this as you are, not so willing to be the actor rather than the act, if that makes any sense.''



``Perfect sense,'' she responded.



``That means I'm not connecting the dots as well as I should.  Instead of wasting your time, I'll be blunt and say that I'm not following.  That's the rudeness I was mentioning.  Can you elaborate?  A living prop\ldots''



``I can't elaborate.  They watch and listen for mention of doors, so they can take us from one stage to the next, and they're listening to every word we utter.  If I continued, it would upset everyone in question.''



``I see.''  \emph{So there's something more.  Something the Doctor is keeping up her sleeve}.



I wasn't surprised.



``I should prepare for battle soon,'' Glaistig Uaine said.  ``Unless there's something else you'd like to discuss, Administrator?''



``There is.  I'm sorry.  My role.  What's my role in things?''



``In this act or in the greater plan?''



``Either.  Both.''



She reached up, placing a hand on the side of my face.  It was warm from the fire.  Her thumb brushed along my cheekbone, the long nail coming dangerously close to my eye.



\emph{She could kill me right here.  Pull my passenger away from me and claim it.}



``I already told you,'' she said.  ``I don't like to repeat myself.  Now come, bend down.''



I bent down.



She gave me a kiss on one cheek, then the other, then stepped back.  ``I look forward to collecting you, Administrator, or to meeting you at the end, if you outlive me.  We can have long discussions.''



``They can talk?'' I asked, looking down at Phoenixfeather.



``No.  But we can \emph{discuss}.  You'll understand, sooner or later.''



I nodded slowly.



``I'm sorry for your loss, Administrator,'' she said.  ``Things become a great deal easier once you realize how temporary it all is.''



\emph{My loss}?



\emph{She knows}?



She stepped away, raising one hand.  Like an explosion occurring in reverse, Phoenixfeather condensed into a point in her hand as she closed it into a fist.



She opened her hands, and two figures flanked her.  Again, the blending of costume and flesh.  The blurring of identity.  Both were women, but one had perhaps been mutilated in death, or she had been a case fifty-three.  She was four-legged, her two arms different lengths.



They worked together to fashion Glaistig Uaine's costume, discorporating the modified prison uniform she'd fashioned into a shroud and reforming it into a proper cloak and robe, with a texture that scintillated green and black, as though it were made up of thousands of scales the size of grains of sand.



I took that as my cue to leave.



``Door.  Chicago Protectorate Headquarters.''



The portal opened.



I stepped through onto the roof of the headquarters.



There was a strong wind, and the heavy clouds of moisture and dust were soaring across the sky.  I looked down, and saw an empty city.  No people in the streets, no moving cars.  During the morning runs, even, or the dead of night, Chicago had been full of life.



I could sense \emph{some} life, though.  I reached out to the bugs that populated the empty city and drew them to me.



I knew why they had placed me on the roof.  Moving the bugs through the building, I could feel the cracks in the structure, the broken concrete, the fallen boards of plaster from the ceiling of the office level.  Something had shaken the building and it was at risk of collapse.



The opening on the roof for flying heroes was ajar.  I sent my bugs inside, all too aware of echo to the event that had led to the ironic case of my joining the Wards.



They collected fabric, collected materials and fit themselves into the channels of my spare flight pack.  Then they made their way up to me, everything on hand.



The swarm circled around me, and they deposited every item, straightening the things out, spacing it evenly around me, a kaleidoscopic pattern..  Spare costumes, costume concepts, weapons, gear.



I'd wondered what form my body would take if Glaistig Uaine were to seize me.  The core costume was the same, but the details, the features\ldots clawed fingertips of Skitter or the extra armor of Weaver's, with a spare coil of silk hidden beneath an armor panel at the back of the hand?



Black?  White?  Gray?  Red?  I had silk bodysuits in every color, from when I'd tested dyes and worn the bodysuits to see how the color held up when the suit was stretched over my body.



What color lenses?



What weapons?



Scion was a different sort of opponent.  Behemoth could be misled by swarm-decoys, one could hide from him.  His attacks were lethal, but most wouldn't tear through cover as though it wasn't there.



There was no camouflage against Scion.  No cover.  A gun could conceivably draw Behemoth's attention for a crucial moment, with a well-aimed shot.  Not so with Scion.



I'd been in a black costume as Skitter, a gray costume as Weaver.  A part of me wanted to go purer, to go white and continue that progression.



But I picked up the black bodysuit.



This wasn't preparing myself for the fight.  We wouldn't be trading blows, and I doubted my costume would be any better or worse than a suit of plate mail or going into the fight naked.



No, I was preparing myself on a mental level.  I gravitated towards the black because it had seen me through the toughest and most personal crises.



It was \emph{home}, for lack of a better word.  I didn't have Brockton Bay anymore, didn't have my dad's.  The black costume was the closest link I had to the last time and place I'd been at home.



White armor panels, to balance it out.



White lenses.



A handgun.  Again, more for the sake of my headspace than for anything else, and because I wasn't sure I could trust everyone present to be on the same side.  Two ammo clips.  It reminded me of Coil.  My first true \emph{kill}.



A taser, for the same reason, and to balance things out once again.  I didn't dislike the added weight of the weapon on my belt.



I donned the flight pack and fixed my hair where it had been mussed up by the straps.



Then, as a final token gesture, I picked up a small canister of pepper spray.  Symbolic.



``Door,'' I said.  ``To the battlefield.''



\sectionbreak



The portal brought us to a small drilling platform, in the midst of the ocean.  No music, no chatter, only the sound of the ocean crashing around us, from horizon to horizon in every direction.  The water was dark, murky, a reflection of the sky above.



Everyone was wearing spider silk.  I recognized the individual components.  Spare costumes, and costumes I'd created and sent out to Protectorate and Wards teams.



A meager contribution, considering our opponent's firepower.



Eighty in all, and we hadn't brought anyone like Rachel or Imp, the people who couldn't contribute to a fight where the opponent could fly like Scion flew, hit like Scion hit.  A dog would never get its jaws on him, and he'd penetrate Imp's defense in an instant, either by seeing through it or by the sheer amount of collateral damage he did.



Lab Rat walked among us, a backpack dangling from one hand.  He handed us devices.  An armband, for communication, earbuds for those of us who didn't have them, and little plastic cases the size of matchboxes, complete with straps.



He was already wearing the full outfit, the wristband over the sleeve of his labcoat, the little matchbox similarly positioned, but over his bicep, like a blank white badge.



He held one out to me, then hesitated.  He fished in the backpack, then handed me another.



``What's the box?'' I asked.



``My work,'' Lab Rat said.



``That doesn't answer my question.''



``You don't want the answer to your question.  Wear it or don't,'' he rasped.  ``\emph{I'm} wearing it.''



He continued on, handing out the packages.



When he was out of earshot, Clockblocker commented, ``I don't think that's a good recommendation.  That guy is \emph{crazy}.  At one point he made himself into some kind of photosynthetic lardass, so fat he took up two stories of a house.  It's the only reason they caught him in the end.''



I looked pointedly at Clockblocker's arm.  The little white box blended in with Clockblocker's white costume.  ``You're wearing the thing.''



``It's a shitty recommendation coming from Lab Rat, but as far as I'm concerned, I'd cut off my left arm if it bought me a better chance.  I \emph{like} knowing there's maybe a chance this would help.  An explanation would \emph{suck}.  Give me a little hope.''



``Maybe that's all this is,'' Vista said.  ``Hope.''



I shut my eyes, focusing on the capes who were present, marking them with bugs.



Here and there, portals opened, and capes stepped onto the platform.  String Theory, carrying only a laptop.  Galvanate.



Galvanate reached out and touched a select few capes.  Layering invincibility over invincibility for Alexandria, for Gavel, Gentle Giant, and a Birdcage cape I didn't recognize.



``Could do with some of that,'' Grue said.



``Borrow his power?''  I suggested.



``Doesn't work.  We did a few test runs before you showed.  Some options.  We'll see.''



Bonesaw and Panacea were both absent, I noted.  Somehow ominous.



``Three minutes.''



Another portal opened.  Glaistig Uaine, twice as tall as she had been, moving as though she were walking, but with no legs beneath swirling tatters of green-black cloth.  Three spirits flanked her, walking on the platform.  Not individuals I recognized.



The wind turned, and I raised my head to let it blow through my hair.  I'd always liked the sensation.



``Why put us out in the middle of the ocean?'' Vista asked.  ``It's crazy.''



``Symbolic,'' a voice said, from high above us.  I looked up to see Legend looking down.  ``Our planet's mostly water.  \emph{We're} mostly water.  It's something you don't really get, being stuck down there on land.''



``Rub it in,'' Clockblocker said.



``Sorry,'' Legend said.



He was a changed man, looking ten years older than he once had.  How much of that was emotional?  The toll of dealing with Endbringers, with being a pariah?  He was respected by the common people, but anyone who knew anything about capes had picked up on Legend's lack of status in the community.



``I never liked locations like this,'' I commented.  ``Rooftops.  Can't get down safely.''



``It's isolated, to minimize chances he can track us somehow,'' Chevalier said.  ``And we have a good escape route.  Not to mention it's the furthest point from Scion.''



When he spoke again, he raised his voice to be sure that everyone on the platform was able to hear.  ``It's time!  This is our staging ground.  We're not going to get close.  We can't, because of the danger it poses, and because the Cauldron capes can't create portals within a certain range of Scion.''



``Can't or won't?'' someone asked.



``It doesn't matter,'' Chevalier responded.  ``This is a test run.  Trying one trick, it won't work.  We'll get obliterated.  So we hit him with things in a series, from multiple directions, and we see what sticks.''



``\emph{I'll be with you every step of the way},'' Tattletale's voice sounded over the earbud.  ``\emph{Defiant's here too.''}



Defiant spoke over the comms.  ``\emph{Take our cues, don't hesitate.''}



Chevalier said something, but I didn't hear it, because Tattletale said something else.  By the reaction of the others, it was something for me and me alone.  ``\emph{And because we're limited in what we can do, I asked to have you in the field, as my liason}.''



``Right,'' I muttered.  I put on Lab Rat's matchbox and then the armband.  A display flashed, and then a request for ID.



``Taylor,'' I said.



My name appeared.  I confirmed.



The display showed what appeared to be a distorted clock, with a square in the center.  The clock had fourteen numbers and only one hand.



``\emph{Fourteen points of attack.  We're alternating strong and weak, clockwise around the dial.}''



One number for each attack.



``\emph{One sec.  Switching String around to keep us on schedule.  Chevalier likes his speeches an awful lot for someone who doesn't like speeches}.''



``-Doors!''  Chevalier finished.



As if corresponding to the fourteen clock faces, the portals opened up in a circle around the platform.



``Ingenue!'' he called out.



Chevalier and Ingenue passed through the door just to the right of the northernmost portal.



He'd taken the lead, the first attack.  He knew there would be too much risk of someone backing off if he put someone else in that crucial first slot.



``\emph{Four miles north of Scion.  Hitting him unawares}.''



The portal door was left open, and my bugs gave me a sense of what he was doing.



Ingenue's power was to muck with other people's powers.  More power, at a loss of control, more control, at a loss of range.  Her choice.



If I had to guess, it mucked with people's heads.  Maybe something to do with their passengers.  Her partners tended to go loopy at some point.  \emph{Homicidal} loopy.



Chevalier's cannonblade grew to three times the size in heartbeats.  Not the gradual growth of before.  It was a wild, reckless growth.  Unfettered by restrictions he'd been held by before.



Ten, twenty times the size.  I'd seen it be as long as Leviathan was tall, and this dwarfed that by a factor of two.



The weapon was too heavy for him to lift.  He let it fall, the serrated blade biting into the earth on the other side of the portal.



He fired, and the combination of the detonation and the recoil wiped out my bugs.



``Second Group!'' I called out, an instant before Defiant barked out, ``\emph{Two!}'' over the comms.



Clockblocker, a Chuckles clone, Gentle Giant and a group of others.



A spread of powers, with mobility and one of the few people who could maybe stand up to Scion's blasts, enhanced by Galvanate's attacks.



They'd be getting dangerously close, using Chuckles' mobility.



I waited.  Waited\ldots  twenty seconds passed.



The world on the other side of the portals rumbled.  Even with portals miles apart, the rumble was felt in roughly equal measure across each of them.



``\emph{Third group},'' Tattletale said.  ``\emph{Big guns.  Watch for collateral damage.  The others may still be there}.''



Pretender, Eidolon and Legend took off, and were soon followed by Glaistig Uaine.



``\emph{He's running},'' Eidolon reported.



``Tattletale,'' I said.  ``Do me a favor?''



``\emph{Anything for you, sweetie.}''



She was being even more offhanded than usual.  Nervous?



``Pass on a message to Legend and Eidolon.  Pretender too, might as well.  They should watch their backs around the Faerie Queen.  I talked to her, and she never quite \emph{denied} she'd help Scion if it came down to it.''



``\emph{On it}.''



I concentrated my focus on the world beyond the portals.  I could feel the bugs on the landscape, the high hills with sharp cliffs, the tall grass that could drown a man, eerily bright beneath a dark sky, with the way the light filtered down.



I closed my eyes, and focused on the senses of my bugs.  I couldn't see detail, but I could make out bright and dark colors.  Scion was bright, and so were his lasers.



An enemy that hit too hard to defend against, too tough to hurt.  Eidolon teleported rather than try to stand up to his lasers, Alexandria took a glancing blow and plunged to the ground.  Legend peppered Scion, paused, then hit him with a bigger laser.



When that failed, Legend doubled down \emph{again}.



``Fourth group.''



The others had already gathered at the respective portals.  This group was Grue, with a select few others.  Shuffle was among them.



Grue looked over his shoulder at me, then saluted.



I felt a lump in my throat.  I wanted to be Taylor, here, but there was a limit to how far I could go with that.



I saluted him back.



As much as I could see the distorted contrasting shapes, I could make out the block of Grue's darkness that Shuffle had teleported into the air above Scion.  It sank down, subsuming the golden man.



Grue fired off a laser, spearing into the midst of the cloud of darkness.



No, not Scion's laser.  Legend's.



If he could use Scion's laser, I imagined he would have.  Legend's lasers weren't doing anything substantial, if they were doing anything at all.  Scion didn't falter, and he didn't act like he was blind.  Alexandria had gotten back up and was fighting at close range.



Scion lashed out with another laser, and some portals winked out before the laser could intersect them and pour golden death onto the platform.



``Grue, return,'' I said.  ``Different tack.''



Chevalier was just returning, carrying a burned Ingenue.  He'd left his Cannonblade behind.  \emph{Destroyed}?



``\emph{Fifth group in},'' Tattletale said.  ``\emph{Everyone else, clear out!}''



Fifth group.  One individual.  String Theory.



``Open one of those portals,'' she said.  ``My lab.  Right in front of the G-driver.  Point the other end at the target.''



``\emph{Clear out},'' Tattletale repeated herself.



Capes at the periphery of the fight were returning.  The Chuckles returned, carrying two wounded capes.  Not even a third of the size of Clockblocker's original group.  Vista hurried to Clockblocker's side.



``He wasn't even aiming in our general direction, and he took out most of us,'' Clockblocker murmured.  ``Fuck!''



Grue's group returned.  Shuffle glanced at me and shook his head.



\emph{One more power eliminated as a possibility}, I thought.



I had to do \emph{something} here.  ``Clock, you leave anyone behind?''



``No.''



``Grue?''



Grue shook his head.



``Nobody left on the other side,'' I reported.  ``String?''



``Idiot!''  String Theory snarled, ``That's not the opening!  Put a portal on the other side of the machine!''



There was a pause.



``Better.  Twenty two seconds.  Use it to give me coordinates.''



``\emph{Patching you into the Number Man},'' Tattletale said.



There was a pause.



The portals all closed, like shutters sliding down, with an ever-narrowing rectangle of light at the base.



We'd left Scion on the other side with nobody to tie him up.  Dangerous.  We couldn't predict what he'd do.



We hadn't, as far as I knew, done any harm to him.  Nothing suggested he had been affected in the least by their powers.  Clockblocker's time freeze, Grue's darkness, useless.



``Give me a view,'' String Theory said.



``Too dangerous,'' Chevalier grunted.  He sat down on the floor of the platform.



``A view!  Now!  Or I'll make it miss!''



A window opened at the platform's edge.



A view of the scene, a landscape torn to shreds by Scion's attacks, grassy fields with steep hills, a fence in the distance, trees on the highest peak.  The grass continued to glow, but some of that was from fires that the fighting had started.



Scion's golden light was distant.  He turned, then began advancing towards the portal.



It was more like the zap from a bug zapper than a shot from a gun.  There was a distortion, like one saw with a shimmer of heat in the air, and Scion was punched out of the sky, leaving behind a golden streak of light.  The path suggested he'd disappeared straight out of the atmosphere.



``\emph{Sources corroborating the visual},'' Tattletale said.  ``\emph{Direct hit.  It worked}.''



String Theory pumped her fists in the air.



``What \emph{was} that?'' Vista asked.



``G-driver,'' String Theory said.  She lowered her fists, then fixed her lab coat and glasses.  She turned around and gave us a smug, superior smile.



``\emph{Which is?}'' someone else asked.



``Upgrade of the F-driver.''



``\emph{The Firmament Driver,}'' Defiant explained, over the earbuds.  ``\emph{At the time of her arrest, String Theory was threatening to use her Firmament Driver to knock our moon out of orbit.}''



``And we didn't hear about this because-''



``\emph{Morale},'' Defiant replied, as if that was explanation enough.



``Would have done a lot for \emph{my} morale to know we could do that,'' Clockblocker said.



``In case anyone was wondering, it's G-driver for God-driver,'' String Theory said.  ``Obviously.''



``Obviously,'' Clockblocker muttered.



``\emph{He's coming back.}'' Tattletale reported.



No surprise.



But we could hit him.



``\emph{Sixth group, ready},'' Defiant ordered.



The sixth group.  Thanda, plus Birdcage capes I didn't know, including one that Galvanate had charged up.  Heavy hits.



We didn't get that far.



``\emph{He's gone},'' a voice I didn't recognize sounded over the earbud.



All had gone quiet, still.



``\emph{Checking cameras, monitoring, radio reports\ldots}\emph{Bastard's hard to keep track of.''}



I felt my bugs stir.  Not the wind.



I looked up.



Scion.  \emph{Here}.  Directly above us, to the point he was barely a speck.



I'd sensed disgust from him once, when he looked at Eidolon.  Nothing measurable, not an expression I could quantify, like a movement of the eyes, brow or lips.  But I'd sensed it.



Now I sensed bloodlust.  Not anger.  Nothing so germane.



Only that sensation I'd had when I was in Lung's clutches and he was squeezing me to death.  The sensation I'd had when Bonesaw was straddling me, carving into my head.  A feeling I'd experienced when I was face to face with Cherish.



A feeling that, underneath it all, there was some base, primal urge to carve people apart.



But he was waiting, watching.



Toying with us.



``\emph{Tattletale},'' I whispered.  ``\emph{He's here.}''



``\emph{No.  Can't be.}''



``We need an escape, now.''



There was only silence.



I felt a kind of grim despair in the pit of my stomach.



``Tattletale?''



``\emph{They're saying no.  Cauldron's saying no.}''



``String Theory hurt him, or at least struck him.  We need others in case they can do the same.  You can't tell me they're going to let us gather some of the strongest capes around and then leave them to die when things take a turn for the worse.''



``\emph{You don't understand.  We put you on the opposite side of the planet, on a different earth.  He wasn't supposed to be able to access you}.''



``\emph{He did}.''



She didn't respond.



One of the Birdcage capes somehow picked up on the same vibe I did.  Maybe they sensed the latent hostility that filled the air and followed it to its source.



They let out a muffled gasp.  Others noticed.



The golden glow above intensified.  Ominous.  Like a second sun, on the wrong side of an overcast sky.



If I was Skitter, I might have tried to sacrifice myself.



If I was Weaver, I might have made peace with the fact that I needed to die, so Cauldron could preserve their portals, maintain the fight.  For the greater good.



I wasn't either.  Not at my core.



``Cauldron,'' I muttered.  ``You're listening, with that creepy omniscient cape of yours.  You're watching.  If you're wondering what you should do, sitting on the fence between letting Scion see your portals up close and track you down or letting us die, let me cast a \emph{fucking }vote.  You save us.''



Nothing.



``He knows already, he has to, if he found us this easily.  Come on.''



``Oh god,'' someone said.  ``Oh god, oh god.''



With my bugs spread out over the area, I couldn't feel a single telltale breeze of a portal opening around us.



I closed my eyes.



``\emph{I'm sorry}, \emph{Taylor,}'' Tattletale said.  ``\emph{I wish-}''



Her voice shorted out as the energy of Scion's attack cut out the communications.





