





``Run!'' I screamed the word.  I took my own advice.



The golden light around Scion had solidified, forming a sphere.  The light dropped.



Others were already scrambling to get away, but there wasn't a place to go.  No portals, no place to run.  The speed and size of the orb made one thing clear.  The people in the center wouldn't be able to move fast enough to make their exit.



I'd been standing in the direct center, to better observe those on the other sides of the portals.  I was one of those people.



I'd spent years running on schedule, interrupted only by injuries here and there, more hectic weeks and a spell in prison.  Years of pushing my limits, pushing myself to move faster, strengthen my legs, build my stamina.  I used it all, pushed myself as hard as I ever had.  The wings on my flight pack extended, and I used the thrusters to give myself some additional speed.



Lab Rat, who had apparently realized the futility of trying to move, wasn't running at all, but was rearing back, a device the size of a baseball in his hand.  He threw it, aiming to put it over the water.



Not enough.  Lab Rat wasn't one of those prisoners who'd packed on muscle in prison.  The ball fell short, then started rolling slightly back towards him.



He swore in a language I didn't know, started to run towards the object.  Too slow.  If he wasn't going to make it over the edge and get to safety, he wasn't going to reach the object.



My bugs hit the object as a mass, rolling it.  It tipped over the edge.  Lab Rat stopped.



The bugs around him caught one word.  ``Angel.''



Lustrum used her power.  It was like walking into a wall, but it wasn't physical.  My brain went blank for an instant, the heat and energy in my body seemed to disappear like someone had flicked a switch.  My power, too, faded, the range zooming to a point close to me, my control momentarily going haywire.  An instant later, it was back.  I staggered, compensated with the antigravity, managed to not fall too far behind.



The sphere above us shrunk a fraction.  Maybe.  Hard to make out, considering the size of it, and the speed with which it fell.  Lustrum, for her part, grew.



I didn't get to see how big she grew.  The orb made contact with the platform, shearing through everything it touched.  My bugs died as the orb touched them, and I could sense the devastation spread as more and more of it came in contact with the structure.



The outermost edges of the orb were still directly overhead, plunging towards me, towards us.



I stepped off the rig, pushing myself off, letting myself fall as I continued moving out, moving \emph{away}.  Falling was good, because it put me further away from the orb.  I'd sooner hit the water than let that thing touch me.



Bugs that couldn't \emph{fall} as well as I could died as the orb made contact.  Bugs that were close to me.  Bugs to my left and right, bugs beneath me.



I felt a momentary disconnect between what I was seeing and what I was feeling.  I felt like I was plunging into the water, everything going numb, pain, my thoughts fragmenting.  Yet I was still fifty or so feet above the water's surface, my view shifting as I veered to one side, despite my instructions to the flight pack.



Lustrum?  No.



I felt increasingly disoriented with every heartbeat.  Couldn't fly.  Spiraling.



Unbalanced.



Blood.



Injury.



I tried to take in breath.  Couldn't.  I felt pain instead.  Right ribs, back, stomach, left buttock, left thigh.



I was falling.  I spread my arms out, trying to slow the descent, failed.



Right hand gone.  Blood, fragments of golden light eating away at stump, making the bleeding worse.



Falling faster, spiraling more.  Thoughts weren't flowing.  I jerked to one side with wind catching wing, spinning abruptly, felt something wrench, pulling from the center of my body.



Fragment of a memory: Legend speaking.  Talking about Leviathan.  Hit water moving fast enough, worse than hitting concrete.



Had to slow my fall.  Most important thing.



There were bugs on me.  I moved them, to get a sense of where I was.  Compare to surroundings.



One wing on pack.



No legs.  Half of stomach left.



The pulling feeling was organs sliding out of body.



Thoughts blurring.



\emph{Help, passenger.  }A plea, an order.



Move arms of flight pack that aren't broken.  Brace against injury.



Wing retracting, propulsion canceled.



Focus on bugs, on antigravity.



Time activation to break spin.  Left, right, match to speed.



Disorientation getting worse.  Two, three seconds where I can't remember where I am.



Focus on bugs.  Only bugs.



Flight pack pulsing.  Rely on intuition.  Starting to feel more pain.  Burning sensations.  Pulling in middle of body.  I start timing flight pack to heartbeat, waves of pain, instead of where I am, direction I'm facing.



Focus.  \emph{Focus}.



Fix position, facing sky, see Scion hovering.  Great smoky shimmering figure stands on water, holding ten or twelve people against arm, tall as oil rig was.



Oil rig collapsing.  Only two legs remain, slumping into water.



\emph{Focus}.



Facing sky.  What was I doing?



Flight pack.



Gravity, push against direction of fall, slow my descent.



Not enough.  Falling too fast.  Need to slow fall just a bit more.



I extended the wing.  Propulsion.



Started spinning again, feel wrenching get worse, spreading through entire upper body.



Hit water while spinning.



No breath left in lungs for impact to take.  Wing breaks, flopping over and over across water's surface.



Stopped.



Sinking.  Use antigrav to try and stay afloat, but system isn't meant to be used underwater.  Can't float because no air in lungs.  Slowly sinking.



I opened my mouth to draw in a breath, had to struggle to manage it, felt intense pain, a crushing in one side.



But I managed to get some air.



Small bubbles spilled out of my side, from beneath the water.



The water around me was murky with blood.



No chance I'd live like this.  Nobody nearby.  Scion was attacking the giant, cutting her to pieces.  Capes she was holding fell.



The rig was collapsing, two pillars slowly falling in opposite directions, one left, one right.  The platform itself was twisting, splitting apart.



So was I.  Half of me gone, the remains slowly leaking out into the water around me.  Blood, fluids, intestine.



I didn't want to die.  Not like this.



Not at all.



I thought about my tools, as if there was an answer there.  My pepper spray?



Delirious, I almost thought about using it on my wounded lower body, some broken connection between burning sensation and burning and cauterizing.



My taser was gone, obliterated by the damage to my side.



My \emph{gun}?



I couldn't manage a laugh, but I would have if I could have.  Thoughts of amusement crossed my mind.  Shooting myself would be one answer, but it wasn't one I wanted to make.



I wasn't ready to die.  Even hovering over Gimel's version of Brockton Bay, I'd tested the limits, stayed out too long.



But now, like this, I knew I wouldn't have let it happen.  I would have fought to swim back, would have called or signaled for help, pride be damned.



Damn it all, I wanted to fight.



Ironic, that I'd be so idiotic when the fight had been taken out of me, but I'd feel so compelled to fight when there was little option besides making peace with the end.



I managed a little breath.



\emph{Just let yourself sink.  Tell the antigravity to cut out, take in one mouthful of water.  That'd be the end of it}.



I couldn't.  I didn't.



But the pain was getting twice as bad with every heartbeat.



Wristband.  Dark.



I didn't have a right hand to press the button with anyways.



Lab Rat's device?



I thought about it, and in that same thought, I recognized a sensation that had been drowned out by the pain.  A repeated pressure.  A poke, a pause, another poke.



I raised my arm over the water, shifted my orientation with a use of one of the antigrav panels, and I briefly heard a beeping in the moment the device was raised above the water level.



A part of the platform fell.  The resulting waves rolled towards me.



I didn't have it in me to hold my breath, so I closed my mouth, prayed water wouldn't flow up my nose.



I was drowned, swamped by the water, rolled.  I felt a dull, indistinct pain in a place that felt disconnected from my real body, something tearing.  The body parts that were spooling out in the water beneath around around me.



I found the surface again.



My lungs were burning for air as I opened my mouth to try and draw air into my lungs.  My \emph{lung}, considering the other might have collapsed.



Everything seemed to be moving in slow motion, my thoughts simultaneously chaotic and focused.  I had nothing left but adrenaline.



Water flowed into my mouth.  I shut it, moved my tongue to help force that same water out between my lips.  Needed to get higher.



Everything was going dark.



The prodding in my arm continued.



Lab Rat's device.  Whatever it was trying to do, my costume was getting in the way.



I couldn't reach up to move it because I was missing a hand, couldn't twist my left hand to move it, because of the limitations of my body.  The attempt at even moving my left arm made me acutely aware of the damage to my hand.  I might have fractured or broken it as I hit the water.



I took in a small breath, forced myself to take in another.  I could hear the wheeze of my lungs and throat straining to work.



And then I used the flight pack to rotate myself, turning myself so my face was in the water.



I floated there, arms extended out to either side, rocking as the waves continued to shift me.



My bugs descended from the air above, landing on me.



The strap that attached the device to my arm wasn't spider silk.  Cockroaches began to chew it.



My lungs burned.  Every moment, even the smallest movement, it redoubled the pain.



\emph{I've dealt with worse}, I told myself.



I couldn't quite believe that, couldn't think back to that, compare, and convince myself.



The water rolled over me.  My cockroaches were washed away.



Again.  More.  Hornets, more cockroaches.



They hovered for the ten or twelve seconds it took me to raise my arm up above the water again.  I let bubbles of air leak out between my lips, as if I could convince my brain that I was breathing, convince my body to hold on just a bit longer, forestall that involuntary gasp.



The device came free.  Strands of silk helped to hold it as the swarm descended, hurried to carry it.



Shoulder.  Back.



Nape of the neck.



Over the hill that was my hood.



They reached the point where my mask stopped, my hairline began.



Vanity.  I'd held on to my long hair, wore a costume that let my hair free.



When I'd been filled with self loathing, when I was so focused on the individual imperfections and the overall ugliness of my features, in the midst of the bullying campaign that had defined my early teen years, I'd still liked my hair.



The skin was exposed there.  No costume to get in the way.



\emph{Please be healing}, I thought, lowering the device until it was against my back.



Pause\ldots and then a prod.



A needle, piercing the skin.



A pressure, as something pumped into my body.



\emph{Heal me}.



It wasn't healing.



Flesh knit together, but it wasn't healing.



The pain faded as quickly and dramatically as it had taken hold, but, still, I wasn't healing.



Not exactly.



My thoughts became clearer.



Water churned where it came in contact with my blood.  Where my flesh closed together and trapped water inside me, the effect intensified.  It was soon the only pain I felt.



\emph{We're eighty percent water, or whatever the number is}, I thought.  \emph{Resources have to come from somewhere}.



Water was seeping into my throat, despite my efforts to keep my mouth clamped shut.



I turned myself over.  I breathed, and it wasn't as hard as it had been before.  My mouth opened, but it wasn't just the lips parting, or the jaw moving up and down.  Things separated and stretched open on a horizontal plane as well.  The soaked cloth of my mask stretched.



My legs kicked, but they weren't good legs for swimming.  I kept kicking anyways.  Something about the way they moved, they were designed so that the motions shifted my abdominal cavity, pumped it, forcing air in and out with the rhythmic activity.



I had to use my hands to paddle myself forward.  Well\ldots one hand and one other limb.  The shape was still nebulous, the growth warring against the steady deterioration of the burning golden energy that still lingered here and there.  It blackened and flaked off, and a little headway was made.



The digit extended, broadened, flattened.



It wasn't fully formed, but it served as a paddle.  I began inching myself closer to the platform.  Easy enough to manage, considering the steady movement of the water.  Things were flowing into some sort of narrow, tight whirlpool, where water was flowing into some hole in the ocean floor.



I shifted my arms in movements that were jerky, not quite \emph{muscular}.  The motions were strong, but hard to control, to moderate.  It was fine.  I didn't need control or moderation here.  I made my way towards one of the intact legs of the platform.  A circle of concrete, cracked by strain, with rebar visible in the cracks.



I pulled myself up, but the attempt was spastic, spasmodic.  I managed to haul myself up, moved a little too far, then fell.



Another attempt.  This time I focused on holding on, bringing my legs up.  One leg in one crevice, another leg into a crack, another set on a ledge where the concrete above wasn't quite seated properly.



My right hand opened, and the motion was more like metal tearing than anything else, tissue parting violently and unwillingly, creating a gap that was as much wound as it was design.



The flesh joined together, forming ridges that faced one another.



I closed it, felt the ridges meet.  The flesh was still tender.  I left it alone.



My flight pack provided additional lift as I climbed.  It was overly heavy, the antigrav weak, but it gave me lift.  I found footholds, handholds for my one hand, and used the arms of my flight pack where I saw opportunities.



I found my stride, scaling the surface with increasing speed, until I was moving faster than I might have covered the same distance running.  My swarm climbed over the surface and provided a map of the places I could find footholds.



I tested my right hand.  The flesh wasn't tender.  It was \emph{hard}.  There were studs at regular intervals along either half, like teeth.  \emph{Very} like teeth.



A claw.



I raised my claw over my head, then drew it down violently, driving it into a crack.



I was able to climb faster.  I reached the point where the concrete ended.  A shaft of four steel beams reinforced by criss-crossing beams set at diagonals loomed above me.



It was an even faster climb than the concrete.  My legs ended in points, and those same points slipped off of the metal beams, but I had seven limbs to work with.  Even if half of my limbs were reaching out for holds, I still had three or four solid points of contact I could maintain at any given point in time.



Rage bubbled inside me, but it wasn't \emph{mine}.  I'd experienced my own anger, I knew how it influenced my own body, how it was connected to my emotions.  This was something else.  Hormones kicking into overdrive, compelling my body to react.  Other parts of my body being \emph{designed} angry, \emph{designed }so they were primed for fight or flight, driving me to act and refuse to let me sit still.



Lab Rat's stuff was geared towards turning people into weapons, making them take whatever forms he keyed into the formula and then \emph{act}.  I knew it.  My awareness of what was going on wasn't stopping it.  I was riding a tide of emotion, moving towards a fight where I couldn't possibly do anything to stop Scion, putting myself in danger.



Had I chosen to, I could have turned away.



But I \emph{liked} being emotional, liked coming out of my shell, acting.



Some of my finer moments had been when I was doing just that.



I reached the top of the pillar and paused.  I wasn't out of breath, and my limbs weren't really built in such a way that they got \emph{tired}.  Still, I had a barrier overhead, now, and I didn't trust my flight pack to hold my weight.  I glanced down, and the individual waves were too difficult to distinguish.  Here and there, there were flecks of white where they crested.



Water still trailed from gaps in the pack as I reached up, folded two tarsus -two `feet'- around a beam over my head, and then swung myself up, grabbing another beam with my claw.  I experimented, testing the security of my grip.  It looked like it could hold all of my weight.  I wouldn't make it do so, but it was a good option.



Movement across the underside of the platform was swift enough.  It only required a different kind of thinking, an abstract sort of grasp of how I moved my legs, found leverage with only one opposable thumb.



A beam came loose as I tried to hang my weight off it, and I nearly fell.  I found leverage on one beam with my third leg, reached out with my hand to grab elsewhere.  Neither hold was secure, but I still managed to swing myself over and seize another beam, securing myself.



I reached the edge of the platform, looked up and over, to see the fighting underway.



Less fighting than systematic elimination.  The only ones who were truly holding their own were Legend, Glaistig Uaine, Pretender and Eidolon.  Even then, they were more focused on avoiding Scion's attacks than dealing damage.  Here and there, Eidolon or Glaistig Uaine would try something.



The remains of the platform had stabilized.  Only a few remained on top.  Weld's people, the Irregulars, made up the bulk of the group.



Sanguine was tending to two injured.  Not Irregulars, but not capes I recognized either.  The boy had hair and skin with a texture and color like clotted blood.  The injured had blood piled and crusted over their wounds, scabs bigger than my hand.  Or my claw.



Weld looked at me, and his eyebrows raised.



I opened my mouth to speak, and found I couldn't.  My tongue was thinner, layered in something hard, and the sides of my mouth were odd.



I communicated through my swarm, instead.  What little of it remained, anyways.  Drones and buzzes and chirps.  ``\emph{Lab Rat.  The boxes he gave us, they're designed to trigger when we're hurt, force a transformation.}''



``Might get a few more recruits,'' Sanguine said, not looking up from the wounded.  He had hands extended to two different wounds on one individual, and was drawing blood into one hand and letting it snake out of the other, flowing into the wound.  Was he cleaning it?



``His \emph{transformations are temporary.  Buying time.  He cut me in half, and I'm not sure I'm going to be in one piece when this stops working.}''



\emph{``}But it worked?\emph{''  }Weld asked.



I nodded.  The motion was jerky.



I reached up with my good hand, the movements twitchy, and felt my neck and shoulders.



The little muscle I had was gone, and the skin was taut over cords, like tendons, of varying sizes.  The muscle had been cannibalized to build flesh elsewhere, I gathered.



Weld frowned, then reached into the pouch at his belt.  He held another device.



After a pause, he pressed it against one of the wounded.



It beeped, then a light went on in the corner.



The cape convulsed, his back arching.



A moment later, transformations began, veins standing out along his arms and legs.



``Another one,'' Weld said.  ``Get me a spare.''



Sanguine handed him another.  Weld applied it.  Scales were manifesting around the most prominent veins on the first one by the time the second patient started reacting.



``Gully,'' one of the other Irregulars said.  ``If we can get to her--''



``We can't,'' Weld said, looking down towards the water, ``But she's wearing one.  I trust her to hold her own.''



Their discussion of how their teammate was doing made me think of others.  \emph{Grue}.  He'd come back through the portal, and he'd been close to the edge of the platform, but that was no guarantee.



It was a hell of a drop to the water, and he didn't have a flight pack.  Not quite something that Masamune had managed to mass produce.



Above us, Glaistig Uaine had created a spirit that was spreading across the sky like circuits on a circuitboard, extending itself across a plane.  Scion was blasting it, but it had reached the point where it was spreading as fast as he destroyed it.  Her other two spirits were working in concert, one duplicating the other, so it could create and lob projectiles that exploded in the air.  The detonations left patches of a strange, nebulous darkness in their wake.  They couldn't move more than a short distance from their master, which limited their number, but they added up to twenty or thirty in all.



``It's working,'' Sanguine said.



It wasn't.  I looked at him, confused.



His eyes were on the patients.  \emph{He's talking about Lab Rat's matchboxes.  }I looked, and I saw how the scales were spreading.  They were breathing easier.



``Good,'' Weld said.  ``We need everyone we can get.''



``\emph{It's a temporary measure},'' I spoke through my bugs, my mouth firmly closed.  ``\emph{Moment this wears off, they might need emergency assistance.  Me too.}''



``Situation's bad,'' Weld said.  ``Not sure we're going to get \emph{any} help, emergency or otherwise.''



``\emph{The Triumvirate came.}''



``From miles away,'' one of the other Irregulars said.  She had a head that was many times the size, a body that was disproportionately frail, to the point that I wondered how she could hold herself upright.  ``They can't open any gates \emph{here} until Scion's gone.''



``\emph{We need to drive him away, then},'' I said.  ``\emph{Or hurt him.  Kill him.}''



The last two words slipped out, so to speak.  Fueled by my anger, my outrage.



No, not quite my own.  A programmed bloodlust, one that came with this body.



``That's\ldots not really doable,'' Weld said.  ``Pretty sure the scientist who knocked him through the stratosphere died.  Nobody else has really been able to knock him for a loop.''



The tendril-girl spoke, her voice harboring a soft Russian accent.  ``We should go, Weld.  Run.  There's nothing more we can do here.''



``There's nowhere to run,'' Weld said.  ``Even if we swim--''



``We're stronger than we think,'' the tendril-girl answered, her voice soft.  ``Isn't that what you always say?  There's a strength inside us and we just need to dig for it.  We came to help the wounded, with Sanguine and Matryoshka.  Let's take the wounded and \emph{go}.''



Weld hesitated.  I suspected I could understand why.



``\emph{I want to help too,''  }I said.  I twitched, as if my body was taking that sentence as permission to \emph{go}.  ``\emph{Murder that fucker.}\emph{But there's only so much we can do.  Go.}''



He gave me a funny look.



``\emph{I was put in charge of ordering people in the field.  Take it as an order from me}.''



``I'm not your subordinate,'' Weld said.  ``And I'm not sure you're in your right mind.  You keep talking in a strange voice.''



``Everything she says is in a strange voice,'' Sanguine murmured.



``\emph{A stranger} voice,'' Weld clarified.



``\emph{Not in my right mind},'' I said.  I stretched.



\emph{Not in my right body}.



I shook my head a little.  ``\emph{But this is the smart thing.  Retreat for now.  This was never supposed to be a prolonged fight}.''



``No,'' Weld said.  ``I'll stay.  I can help others.  I'm tough enough to walk away with most of my body gone.  I'll search for others who need help.''



There was the mask again.  Even the case fifty-threes had them.  The emotional defenses, the guise.  He was hiding something, lying without speaking falsehoods.



``\emph{Go},'' I said.  There was an emotion in the sound there really shouldn't have been.  Anger.  Irritation.  Insofar as I could even express that with a voice generated by my bugs.



He hesitated.



Scion erupted with golden light.  It wasn't the sort of attack one dodged.  Instantaneous, hitting everything in every direction.



My skin began to blister, the golden light searing through it, appearing in the ridges between spots where flesh was simply being eaten away.



I scrambled for cover, moving back towards the underside of the platform.  As I leaped over the railing, I grabbed one of Sanguine's patients with my claw.  My movement was reckless, too quick, unpracticed, and I nearly threw the cape I was holding over the edge.



I waited, hanging by my three legs, two flight-pack arms, and one hand, the cape dangling below me, gripped in my claw.



The light faded.  I checked, then climbed back over the edge.



Weld and his people had taken cover.  Sanguine was covering injuries with scabs, but the damage was bad.  The tendril girl's tentacles were worn so thin they were barely there.



The cloud cover had been largely dissolved, bringing more light down onto the battlefield.  More to the point, Scion's likely target had been affected as well.  The cape that had spread across the sky was falling apart.



Scion turned his attention towards Glaistig Uaine.



Eidolon appeared beside her, taking her in his arms, and then the pair of them disappeared just as quickly.  Legend opened fire with a series of lasers, while Alexandria ducked around to get behind the bastard.



The cape I was holding climbed over the railing.  I made my way under it, then sort of staggered in Weld's direction, the tarsus segments of my legs sliding on the slanted, gritty surface.  The light had eaten through metal, eroded everything in sight.



Below us, the water had been affected, boiling.  Clouds of steam rose from the water's surface.



My thoughts turned to the capes below us.  My friends, past allies.



Murderous instinct flared, and I restrained it.



``We need to \emph{go},'' the tendril girl said.  ``We're no use to anyone dead.''



``I can't swim, Sveta, understand?'' Weld's voice was quiet.  ``It's not- I'll stay behind.  We've got the case for you to hide inside.  Sanguine can carry you.  You should go.''



``We need you, Weld,'' Sveta said.



Weld looked away.



``Another form,'' Sanguine said.  ``Something that floats.''



``I'm metal.''



``Metal boats float,'' Sanguine said.



Weld frowned.



``What is it?'' Sveta asked.



``I'm not sure it'll work.''



``If it doesn't,'' Sanguine said, ``\emph{walk}.''



``On the ocean floor?''  Sveta asked.



``He doesn't breathe.''



``It's not that simple,'' Weld said.  ``I'm going to stay.  I have old teammates to look after.  You guys should leave.''



``Not without you,'' Sveta said, her voice angry.



A golden light speared past us.  Striking the water.  Scion was cutting up the capes who'd fallen in and survived.



Glaistig Uaine appeared behind him.  Three spirits surrounded her.



One to levitate, grant the ability to float.  A telekinetic or power granter.



Another to duplicate capes.  Duplicating the telekinetic, in part.  But more focused on duplicating the third spirit Glaistig Uaine had made.



Gray Boys.



She'd gone through a phase, hunting down some of the scariest capes around, defeating them, claiming them.



This was one.



Scion was trapped in a time well, turning monochrome.



Without any apparent effort, he broke free of the effect, shattering it.



Only to be frozen again.



My swarm was agitated.



Agitated but futile.



Scion started moving in the direction of Glaistig Uaine and her creations, gliding through the air.  The effects went up as easily as they were torn down.



I wanted to help.  To stop him.  I was powerless.  \emph{A cockroach}.



Glaistig Uaine wasn't stopping him, but it seemed to have his attention.  He wasn't using his power, either.  Was it because he couldn't, or something else entirely?



Eidolon, Legend and Alexandria flew down to the water.  They rose with no less than twelve capes between them, Eidolon levitating several, and then disappeared towards the horizon.



Weld seemed to come to a decision.  ``Okay.  If it's what it takes to make you guys leave, I'll go.  Make our way down.''



I shut my eyes, exhaled slowly.  The air moved in a funny way across my mouth-parts.



``\emph{Here},'' I said.



I reached for my belt.  It dangled, held in place by the silk cords that wound under and beneath my costume.  Some of it had been obliterated by the blast.  I used my bugs to start connecting the silk cords together.



Too thin, too short.



I reached behind my back, instead, past the small tube of pepper spray.  More silk there.  Some beneath the armor panel on my hand, others beneath my shoulders.



I plaited them together into a rope.



``Others go down first,'' Weld said.  ``Order of weight.  Let's get you packaged up, Garotte.  If you aren't climbing down, stay still.''



Stay still?



He began undoing the little clasps of metal that bound Garotte against his body.  She unfurled, reached out to railings, to edges of metal.



Where the tendrils surrounded the railing, a barrier that might have stopped a speeding car, the metal bent, crushed tight.



The tendrils continued to find their way to things to grip.  There were more of them than I'd thought.



One tendril seized my claw, faster than I could react.  Just as fast, it pulled back, found somethign else to hold.



She and Weld both stopped.



I watched as she closed her eyes, drew in a deep breath, and then exhaled.



Weld released her organs, hidden in a space in his broad back, and she was free of him.  She collected herself around the railing, her eyes closed, drawing in deep breaths and then exhaling slowly.  Slowly, the tendrils released, and she stretched out to her full length.



She looked like a fish underwater, a lionfish or jellyfish with dramatic, crazy fins or fronds.  Where they weren't bound to her surroundings, the fronds fell in line with one another, moved with their own rhythm, a mind of their own, that searched the surroundings.



``Tight, Garotte,'' Weld said, an order.  His eyes weren't on her, but on Scion and Glaistig Uaine.



Garotte wound herself around the railing, weaving her tendrils into gaps of the platform itself, to seize infrastructure.  It was beautiful in a very different way, sinuous like a snake was, a face with everything condensed behind it, a mobile, flexible body.



Scion and Glaistig Uaine began fighting in earnest.  They weren't more than a hundred feet apart.  Glaistig Uaine was drawing on spirits with a shorter range, now.



One with a fox-face that seemed to be granting three different kinds of enhanced movement, teleportation, super speed and flight.  The other two varied from moment to moment.  Some existed so briefly that Glaistig Uaine didn't even try to keep them afloat in the air, images that lasted two or three seconds, employing their powers before they exceeded her natural range and dissipated.



Some came back, used powers in different variations.  The ones Scion destroyed, though, they didn't recur.



Glaistig Uaine was running out, and running out fast.



Weld patiently helped Sveta bind herself to a single pole inside a half-sphere the size of a beachball.  When she was inside, he attached another half to the sphere and began screwing it shut.



Here and there, the smallest tendrils found their way out of airholes.  They gripped his hand.



``Be brave, Sveta,'' Weld murmured.



``I just tell myself I need to act like you,'' Sveta's voice came from within the sphere.



Weld didn't answer that.  He handed the sphere to Sanguine.  The red-skinned boy gave his leader a nod, then started sliding down the length of the cord.



The capes who had taken Lab Rat's juice were among the largest.  They descended the rope I'd created.  Only a couple were left, now.



``Matryoshka, get the ones from inside,'' Weld said.  ``Think you can manage?''



A young case fifty-three with horizontal lines marking the length of her body nodded.  She began dissolving into ribbons as she made her way across the platform.



``You're not coming, I suspect,'' Weld said.  I realized he was speaking to me.



I shook my head, the motion jerky.



``If it's about the injuries, the juice wearing off, we can support you, give you some healing.''



``\emph{Not that}.''



``There's nothing you can do.  Nothing we can do.  Any of us.''



``\emph{String Theory hurt him.}''



``String Theory died.  And she didn't hurt him so much as shove him.  It's like a three year old pushing a grown man.  Right time, right place, catching him off guard, nothing more.''



The metaphor was eerily similar to Shadow Stalker's one about cockroaches.



``\emph{I'm talking abstracts,}'' I spoke through my swarm.



I watched as a very androgynous figure left the building Matryoshka had entered.  She bore innumerable injuries, but stoicly limped her way to the rope, gripping it.  She glanced at Weld, then nodded.



``Abstracts.''



``\emph{We know it's possible to shove him, maybe other stuff is possible too.  There's hope}.''



``So you want to do this again?'' Weld asked.  ``How many of your friends came?  What did you stake on this?''



I thought of Grue.  I didn't know if he was okay, or if he was one of the capes who had been in the water.



``\emph{One came,}'' I said.



``Is he okay?''



``\emph{Maybe.}''



``I brought everyone, lost three for sure, one that's a maybe,'' Weld said.  ``You don't-  we can't do this again.  He's too strong.  Unstoppable.''



``\emph{You wanted to stay},'' I said, stressing the \emph{you} as much as I was able, speaking through the bugs.



``No,'' Weld said.  ``I didn't want to leave.  Different thing.''



I didn't have a response to that.  Legend, Alexandria and Eidolon had returned.  Legend and Alexandria rescued more stranded capes, flying off, while Eidolon rose into the air, positioning himself so Scion was between him and Glaistig Uaine.



``Sveta idolizes me.  She sees me as a hero, a spokesperson for our kind.  Her therapist asked me to come visit, because she heard about what happened in the Echidna attack, what Cauldron was doing.  All of her progress, gone.  So her therapist wanted her hero to show up.  Give her guidance, support.  It worked.''



``\emph{That's a good thing, isn't it}?'' I asked.  I saw Eidolon open fire, not a dramatic attack, but a subtle one, a series of darts that left dark streaks in the air.  My entire body tensed, as if I could jump into the fight.



Weld was shaking his head.  ``She thinks I'm fearless, but I'm not.  I don't have any hormones, any real heart that can pound, adrenaline to flow through my veins.  But I still feel fear, still feel despair.  I can't jump into the water and sink to some point lower than mount Everest is tall, spending months or years without any goddamn music.  So I stay here and\ldots I try to convince them to leave.  I'm a coward in the end, putting them at risk because I'm scared I'll sink.''



``\emph{They left,}'' I said.



``Because I lied.  I'm not going to follow them.  I'm staying.''



I nodded.



``Sweet fuck all we can do, you know.''



``\emph{I know,}'' I responded.  ``\emph{But nothing we can do except fight.}''



``I don't know if I should pity you for that perspective or envy you.''



I shook my head.



Weld spoke, his voice grim.  ``In terms of morale, there's no fixing this.  We put our best foot forward, we failed.  I can't speak for the others, but I can guess how they're going to feel.  I think of myself as a brave guy.  I pulled off the hero bit, I lead by example.  But I don't think there's anything we can do but run.''



``\emph{That's all you'll do from here on out?  Run?}''



He looked down at his hands.  ``And get revenge.  I promised other people we would.''



``\emph{That's the opposite of what we need to be doing, Weld.  You have to know that.}''



He looked up at me with inhuman eyes that were framed by fine wire eyelashes.  His expression communicated so much, considering it was hard metal.



``\emph{Give me a chance to prove otherwise,}'' I said.



``Prove--'' he stopped mid-sentence.  ``Prove what?''



``\emph{I don't know,}'' I said.



Then I moved, hopping up onto the top of the nearest structure, a small building that had stood on the edge of the platform.  My bugs stirred around me.



\emph{You took my dad from me, my hometown.  You took our hope, betrayed humanity}.



\emph{I don't do well with betrayal}.



As I moved along the platform, I got a view of the last of the Irregulars making their way into the water.  Fallen debris was keeping them from being dragged into the narrow whirlpool beneath the structure.  They swam as a group, some using pieces of wood for flotation.



They just had to get far enough away from Scion for someone to open a door.



My swarm climbed the rope, taking it apart, for multiple strands.  They formed a single cord that was thin, but a quarter of a mile long.



Me, my passenger and my screwed up monster body were all in agreement.



\emph{I want to hurt him}.



\emph{Want to prove this isn't hopeless, that we can do something.}



\emph{I don't want to lose to another bully.}\emph{I'm done with surrendering to }forces of nature\emph{, human nature or otherwise}.



My swarm extended in his direction, carrying a strand.



I hurried across the length of the platform.  Who was still here?



What could I do?



Nobody of consequence on the upper level.



Down there?



Drawing out a cord of silk between me and the railing, I used my faulty flight pack to lower myself towards the water.



Silk wound itself around Scion's eyes.  He didn't pay it any mind.  His focus was on Glaistig Uaine.  Her spirit was the same one she'd used before, launching ineffective attacks that left blotches of darkness across the sky.



I found the capes on the water.  A Thanda, three birdcage capes.  The Thanda was using his power to fix them all in space, so they stood just a short distance above the water.  Two of them recoiled in fear as I lowered myself to their level.  The Thanda was calm, by contrast.



The wind blew the silk, threatening to pull it from my grip.  Scion was moving, and it could break at any instant.



I passed the silk to the Thanda.



He gave me a curious glance.



Then he froze it in space.



It fixed the thread's location in space, froze Scion as well.  The golden man was rendered immobile.



Glaistig Uaine, Legend and Eidolon all struck him with everything they had.  Attacks too big or too slow to land otherwise.



I collected the remains of the silk before it could land in the water.



Not enough length to use the Thanda again.  I moved, relying on the flight pack.



It shorted out, and I used the sole remaining panel of antigravity to land on a shattered corner of the oil platform.  It was slowly sinking into the waves.



The swarm.  Not many bugs, but \emph{something}.



I'd thought he was perceptive enough to see through the decoys, but he \emph{was} the golden fool.  The Simurgh had deceived him before.



Maybe it wasn't that he could draw the logical conclusion and know that there wasn't a human inside.  Maybe he was too ready for breakers, for capes who didn't follow the usual rules.



I created a swarm decoy, gathering all of the bugs from the surrounding area.  I couldn't tap the resources beneath the water, but I could draw from the life that had gathered on the rig, the bugs that feasted on the algae that clustered around the legs of the structure.



The body approached, and Eidolon moved aside.  He moved as if it were a comrade joining the fight, as if he, Glaistig Uaine and the swarm-decoy effectively had Scion surrounded.



Idiotic, nonsensical.  Scion didn't even react to the maneuver.



Glaistig Uaine attacked, and Scion retaliated.  Her spirit teleported her away.



Eidolon created mirror images of himself, illusions, and Scion lashed out.  Only one of the illusions remained.



It fizzled out.



\emph{Eidolon died?}



No.  Eidolon struck out from the clouds above.  Scion seemed to anticipate it, sliding out of the way.



The tempo of the attacks and counterattacks continued.  Scion attacked Glaistig Uaine's spirits, and still, the destroyed ones failed to return.



A pattern?



He was an alien combatant, a stranger from another world, who saw the world in an entirely different way from how we did.



But there was a pattern.



I divided the swarm decoy in two.



Divided each of those two into two more.



He'd stopped the spirit from spreading across the sky, and had made a concerted effort to eliminate Glaistig Uaine's spirits.  He'd eliminated Eidolon's illusions.



Whether the creations were concrete or otherwise, it was something that seemed to provoke him.



Was it something instinctive?  A part of his species?  Something he watched out for in enemies, in threats or competition?



Scion turned and blasted the swarm out of the sky.



The last of my bugs.



His hand turned my way, as he floated in my direction.



He knew who was controlling them.



It was a diversion, a crucial distraction.



Glaistig Uaine flew in close, creating another set of spirits.  Two to either side of her, one in the lead.



I recognized the one in the lead, distorted as it was.



Clockblocker's spirit touched Scion, and the golden man froze.



She banished the ghost in an instant, recreated the one who had created the dark blotches in the sky.



The blotches began to move, gravitating towards Scion.



Concentrated in one spot.



\emph{She plotted this, planned out the extended attack}.



I felt my hair stir, drifting towards that spot.



I'd seen something similar, once upon a time.  I backed away until I was able to grab something for a hold.



They all gathered into a single dot, and the effect intensified.



The effect around Scion broke, and he began drifting towards the dark point.



He resisted, and I could sense something from him.  Not \emph{alarm}, but a reaction nonetheless.



From Glaistig Uaine and Eidolon's body language, they saw it too.



He reached out, one hand stretched towards the center of the effect.



And Eidolon used a power, effectively detonating the effect, reversing it.



The G-driver had sent Scion flying into the atmosphere.  Eidolon had apparently taken a lesson from it, because he'd emulated the effect.  Here, Scion was plunged into the water.



Another hit, another inconvenience.  \emph{Something}.



He was in the water.  He'd come back up.



We could do it again.  I just needed to form another decoy.



Except I'd used up every bug I had on this.



Not bugs, then.



I flexed the legs that Lab Rat's serum had given me, then dove into the water.  I held my breath, making my way deeper.



It was negligible, but I wanted as many as I could get.



Simple lifeforms.  If there were none above the water's surface, I'd use the ones below.  A glance above me showed one of the flying heroes above the water's surface, watching.  Good.  We'd be able to coordinate an attack.



We were too far from the ocean floor for me to find crabs or lobsters, but there were others.



Krill.  Two inches in length, at best.  But they were alive, and I could move them.  I could use them.  Another swarm decoy, another combination attack.  Something that-



My claw twitched.



I closed it, then flinched.  The `teeth' of the claw had bitten into soft flesh.  It hadn't been soft before.



I kicked, and I could feel the lack of strength in the leg's movement.  The spasm wasn't as strong, and a wet feeling was running along the inside of the leg.  Fluids leaking.



No.  I wasn't going to stop.  Not now, not like this.



He'd have to surface, he'd be angry, distracted.  There could be an opening.



I kicked, paddling myself forward, and I wasn't moving towards the surface  Just the opposite.



My lungs were feeling the strain.  I didn't care.  He'd come up, and we'd-



Crimson blossomed across my vision, obscuring my view.  Blood.  Mine.



One leg came free of the socket.



\emph{No}.



Piece by piece, I started to come apart.



\emph{The decoy.  If I keep it together until he comes, let them split apart naturally, maybe he'll be fooled.}



I started to try and move towards the surface, aware of my circumstance.  My strength wasn't there.  My muscles had been cannibalized for parts to build this temporary body, and the reversion process wasn't supplying them with everything they required.



My flight pack failed.  I couldn't raise myself to the surface.



\emph{Let me prove we can fight back.  Don't let people like Weld give up at this point.}



My consciousness began to dim, faster than it had before.  I didn't have the benefit of adrenaline.  I had desperation, but it wasn't quite the same.



My vision gradually fogged.  I felt my body going numb.  My arm, my face.



Water began to fill my mouth.  I didn't have the strength to keep my lips pressed together.



\emph{Let him rise to the surface.  Let this trick work again and again.  Let it be the Achilles heel.}



A false hope, a faltering one.  I knew it wouldn't work again.



I coughed, and it was a weak cough, barely a hiccup.  Enough for water to make its way into my throat.



But I focused on the swarm, on the krill.  Kept them in formation.



\emph{Alexandria died like this.  Drowned.}



A shadow passed over my vision.



I forced my eyes to focus.



Glaistig Uaine, smiling slightly.



She'd been the one above the water.



And here she was.  Not helping.  Waiting.



\emph{At least I'll still be able to contribute}, I thought.



The water moved, and I saw a look of disappointment on her face.



A glance to my right showed a portal.  A door.  The water was flowing into it in vast quantities, and I was being pulled along.



\emph{He's gone.  He's nowhere close}, I thought.



\emph{We won't recover from this}, I thought.  \emph{Won't pull together with this kind of strength again}.



\emph{We lost}.



I blacked out.





