





\strong{June 24th, 2013, now}



``He returns,'' Glaistig Uaine spoke in her chorus of voices.  Were there less voices in there than there had been?  She was dripping wet, having just ascended from beneath the water's surface, but a spirit was attending to her, drawing the moisture forth, coiling it into wreaths and ribbons that trailed around the Faerie Queen and the other spirits.



Eidolon stared out at the horizon.  He could sense the shift in air pressure, see the movements in clouds and water alike.  Scion wasn't any bigger than an ordinary man, but the world seemed to react to his existence.



``I know,'' Eidolon answered, belatedly.



Something crumbled beneath them.  The oil platform wasn't designed to stand on two legs, and it was deteriorating under the stresses.  Eidolon could feel his pulse quicken, excited despite everything.



Excited, despairing, hopeful, hopeless.  He had no idea what to do.



He had a mission.



He'd never been one for drumming his fingers, for pacing or biting his nails.  He had never gotten in the habit.



Eidolon closed his eyes for a moment, releasing his hold on the sensory power.  Like something swelling within him, filling every available space, another ability took hold.  Something defensive.  An invisible bubble surrounded him, linked to another power.  Teleportation.



It was a strong defense against aimed attacks, but it wouldn't help against something indiscriminate enough.  He had a matter creation ability that was perhaps worth trying, and he had a density warping ability that could perhaps deflect blasts while letting him stand on the air.



He was reluctant to give up either of them.  Both were options, possibilities.  Warping of time and space tended to have an effect, so the offensive power was a good one to have on hand.  The density warping ability was key to his staying airborne.



Flight was too important, but it was an ability he had in shorter and shorter supply.



``Can I assist you, High Priest?''



He opened his eyes. \emph{ High Priest}.  ``I need more abilities than I have.  There is a hole in my defenses.  To cover it, I'd need to give up my flight, or give up my offensive power.''



``Not a concern.  I'll carry you.''



He hesitated.



``Let go of the flight,'' she said.  ``I'll catch you.''



He glanced down, and he couldn't make out the individual waves.  That wasn't because of the fog that still lingered after Scion's disintegrating glow, but because of distance.  The occupants of the platform weren't visible either.  A drop from this height would be fatal.



He could survive it if he manifested the right ability.  He might not have given it a second thought if it was only a question of his power's reliability or only a question of Glaistig Uaine's allegiance, but the two together gave him doubts.



He looked at her.  Her clothing was dry now, animated by the wind around her, like the limbs of an octopus, green where the light caught it and black otherwise.  Thin streams of moisture surrounded the garment, complementing her form, enhancing the unnatural appearance.  A human face in the midst of an alien, abstract form, her eyes far older than the flawless, childlike face.



Her stare transfixed him.  He couldn't even guess at her motivations.



Scion, the Endbringers, they were the others who typically came up in the same breath as Eidolon.  He was the only one of them that was human.  He had less power than they did, but more power than most.



Glaistig Uaine was one of the others, a contender for the title, though not necessarily in the public's perception.  The PRT had controlled how much information the public had about her, to keep people from getting too scared.  She was a nonfactor, a captive in the Birdcage.  She'd taken down Gray Boy, had attacked the King's Men and slain Athrwys, and then she'd turned herself in.



Easy enough for the average Joe to dismiss her as a lunatic.



Except Glaistig Uaine had been amassing power during her time in the Birdcage, and he had been losing it.



Had he been supplanted in his role as the most powerful person in the world?



``A leap of faith,'' Glaistig Uaine spoke.  ``Give up your power and I will be able to lift you.''



He glanced at her.  She was smiling a little, as though she'd said something amusing.



``Can you tell me why you call me the High Priest, before I put my life in your hands?''



``I could say it's because you rely on a higher power for your strength,'' she said.



``You could.  But \emph{will} you say so?  Because when you talked about the others, you were speaking about their \emph{faerie}, their passengers, their agents, not the individual.''



``Yes,'' she said.



He remained still, inviting her to elaborate.



``Some lead by logic, by law, by order and organization.  Others lead by the abstract.  By faith and the imagination of the public.  Yes?''



``You're talking about leading\ldots the passengers, the agents?''



``Naturally so.  Plotting, raising the faerie up as objects for worship.  They are chosen, \emph{cultivated}, as the situation demands, to suit the world outside, to best manipulate it.  The pantheon in the temple.''



``Me.  I'm this temple?''



She nodded.  ``Mmm.''



He frowned behind his mask.  His voice was just a touch harder than it had been.  ``This `High Priest' you speak of doesn't sound like any priest I know.''



``I have little love for gods or the godly, High Priest.  I may have to apologize for choosing such an unflattering title to describe you, but it fit as described, fit on other levels.''



``Other levels?''



``I would continue, but then we'd run out of time.  A minute, perhaps less.''



``You seem to know a dangerous amount, Glaistig Uaine.''



``And you know dangerously \emph{little},'' she responded.  ``We're out of time.''



The statement was ominous.



New powers took time to take hold and build up to full strength.  As of late, it was taking longer, one of the areas where he was growing weaker.  Could he trust her to catch him?  Or would she let him fall to his death, attacking him if his powers saved him, just to collect his abilities and add them to her own?



Was it maybe \emph{better} to die?  Perhaps she could make better use of his remaining power.  Or perhaps passing his power on to another individual would fix things, reset the gradual losses.  The Eidolon-clone that had been created in the Echidna attack in Brockton Bay hadn't seemed as restricted.



He released his hold on the flight power, thinking of the broad-target attack that had eliminated \emph{Granka's} spirit, scalding everything in sight, disintegrating the spirit's branches as they reached across the sky.  He could only hope he got something suitable.



Eidolon fell, tumbling head over heels.



\emph{Perhaps High Priest is fitting}.



\emph{My life, always in the hands of greater powers.}



\blacksquare



\strong{December 5th, 2012, six months ago}



He stood from his seat, fists clenched.



His powers were adapting.  He'd been holding on to them, but the anger and circumstances were apparently enough to force a shift.  A perception ability, an offensive ability that would let him move objects violently along strict paths that were dancing across his field of vision, and a future-sight ability that was making the world change colors, identifying points of high future stress and danger with colored blotches.



Doctor Mother was so unthreatening that she might as well have been absent.  A shadow in the midst of the lines that continued spiraling out in every direction from every inorganic object in the room, each flaring with color.



Contessa remained still, but she was highlighted in danger.  Her breath fogged in the air as though it were winter, but it was merely the abstract representation of danger.  Her lips, her eyes, her hands.



The Custodian, as well, loomed.  There but not there, filling every space in the complex, moving not her physical body, because she had none, but her focus, as if that were a concrete object.



The telekinetic smash would let him move her aside.  Contessa\ldots he couldn't beat Contessa.  The precognitive power he'd gained wasn't one he'd used before, but he knew.



The precognitive power, apparently useless in this circumstance, disappeared.  Another began manifesting.  Something abstract, offensive enough to level the entire complex if he needed to.



Equally useless.  She had an answer to that as well.  The ability to see danger as colors still lingered, disappearing as the other power grew.  Any fading in the color around her was solely because he was losing the ability, not because she was any less dangerous.



Idle thoughts.  He was angry, the desire to harm them in retaliation was one his agent responded to, but not one he would act on.  Frustrating, that the distinction was lost on the agent.



``Say it again,'' he spoke.  He let his voice tremor with the power that surged through his body.



``I can't, in good conscience, give you another booster shot.  They're getting less and less effective in terms of how long they last and how robust the effects are.''



``It's still having an effect,'' he answered.  ``Small or otherwise.  The Endbringers are attacking every two months.  Paris was just two weeks ago.  You can't deny I helped.''



``Scion won that fight, Eidolon,'' the Doctor responded.  Her voice was gentle, patronizing.



He clenched and unclenched his fists.  ``You can't do this.  The number of lives I save\ldots''



``It's substantial.''



``You're asking me to leave them to \emph{die}, Doctor,'' he said, and the words had a bite to them.  ``You \emph{don't} want to look me in the eye and tell me that.  Don't betray me by telling me you're now going against everything we've been working towards.''



``I'm asking you to leave it to others.  Each dose we give you is a formula we're not giving another person.''



``Nothing you ever said suggested that quantity was limited,'' he said.  \emph{I know it isn't.  I used a power to put the numbers together.}



``It isn't limited.  Not to the point that we'd run out in the foreseeable future.''



``Then I don't see the problem,'' he said.  He leaned forward, gripping the table's edge.



``The formulas take some time to create.  Gathering the raw materials, getting the balance right, twelve minutes on a good day, thirty on a bad, only to provide a booster shot that doesn't last two days?  That gives you a ten percent boost to your abilities and manifestation times?  At \emph{best}?''



``It's \emph{meaningful},'' he growled the last word.



``It has to stop at some point, Eidolon.  I have to draw a line in the sand and say that, at some point, you're going to have to adjust.  That giving a formula to someone else for that one-in-a-thousand chance we get something we can \emph{use} is better than having you be marginally stronger.''



``You can't-'' Eidolon shook his head, changed tacks.  ``Doctor.  I've always been on board.  You told me about the true goals, about the experimentation, I was loyal, I understood.   I know what we're up against.  The rate of parahuman growth, the number of villains, the Endbringers, the end of the world\ldots''



``I'm not debating that,'' the Doctor said.  ``I'm saying it's more efficient, and we \emph{have} to be efficient now.''



``More efficient.  Says who?''



``Contessa.''



``\emph{Fuck} Contessa!''  He leveraged the telekinetic power, slashing his hand out to one side. The desk moved like a bullet-



-And stopped, no more than a hair from the wall.



The Custodian, invisible but to his other senses, gently set it down.



Eidolon hung his head.



Once upon a time, she wouldn't have been able to stop him.  If it came down to it, he could attack her, drive the Custodian away.  He could see the lines.  But that wasn't the important thing here.  It was another reminder of how he was getting weaker.



The Doctor spoke, ``I should have listened to her sooner, but there are too many blind spots around this situation.  The Endbringers, the End of the World, the formulas.  Things she can't see.  I held on, told myself I wouldn't cut you off until we had another Simurgh attack, to ensure you could minimize the damage, that you'd be able to recuperate and adjust for at least a few months before she showed up again.''



He shook his head slowly.



``The Guild found the mass-production tinker.  All signs point to them becoming a force in their own right.  We won't be helpless.''



``No,'' he said.



``This is for the best, Eidolon.''



``If it's a question of labor, can we divide the task?  Get more hands on the job, for making the formula?''



``It's not worth the risk.  We'd be risking another Manton situation.''



``With Contessa's ability, though?''



``It didn't allow us to know about or prevent the Siberian from coming into existence.  It's a blind spot\emph{.  }If we \emph{must} take risks, then we need to be smart about it, ensure we limit it to the risks we \emph{need} to take.  Gambling on creating deviances, outside cases or others.''



``You asked me for my trust, I gave it.  You asked me for loyalty, I gave that to you as well.  You asked me for sacrifice, and I gave that.  I was content to be second place in the Protectorate, because it's what you needed.''



``What Alexandria needed.''



Eidolon shook his head.  ``Let's not pretend.''



The Doctor paused, then nodded slowly.  ``Fair enough.''



``When the shit hit the fan, when my clone divulged the ugly details to the public, I made sacrifices there too.  I walked away, so the Protectorate could stand.  Gave up \emph{everything}.''



``And I'm afraid I must ask you to give up \emph{this} as well.''



``\emph{This} is all I have,'' he said, his voice quiet.  ``It's my career, my life.  It's my \emph{legacy}.  Some have children, flesh and blood to carry on their name and their memories.  I went without, for your sake, for the \emph{world}\emph{`s }sake.  I didn't have children because I wanted to save lives more than anything else, and if I made peace with that, it was because I told myself this would be my legacy.''



He realized he was staring at the floor, raised his head to meet the Doctor's eyes.  She was managing to look sympathetic.  It pained him.



``I'm not- being famous was never a focus.  I never begrudged Legend his status in the Protectorate, never put my status or any of that above saving lives.  Understand that.''



``Oh, I understand,'' the Doctor said.  ``It hasn't always been pretty, but you've never wavered.''



He pulled off his mask, letting his hood fall down around his shoulders.  His face was briefly reflected in the reinforced mask.  Homely, balding, with heavy cheeks, lines in his face from stress.  A nose and ears that were too large.



``Maybe I'm not a good man, but I hope the people I've saved can do enough good to make up for that.  Does that make sense?''



``Yes,'' the Doctor said.



``So I hope you don't mistake me.  I hope others don't mistake me, when I say that it does matter, still.  The legacy.  That I want people to remember me at my best, not as someone withered.''



``Do you need to sit, Eidolon?''  The Doctor asked.  ``David?''



He shook his head slowly, but he took the seat, using his telekinesis to move it left, then forward, until it was right behind him.  He collapsed into the chair.



The Doctor took her seat at the chair that had been behind her desk.  Confident, prim, proper.  The one with the answers, even if he didn't \emph{like} those answers.



Priest and confessor.



A silence lingered.



``With the table gone, all this empty space between us, I'm put in mind of a psychiatrist and her patient,'' the Doctor said, echoing his thoughts.  ``I'm not that kind of doctor, though.  I'm not equipped to give you that sort of answer, David.''



``No.  No, I know that.''



``When all of this started, we made an agreement.  I made only one promise.  I can't betray that promise for the sake of your legacy, for anything.  Not even if it means saving \emph{you}, saving \emph{any} of us.''



``I know.''



``I can hear you out if you need to talk.  As a friend, as an impromptu therapist, whatever you need.''



He met her eyes.  There weren't tears in his eyes, but that fact was more surprising than not.  He \emph{felt} like he wanted to cry.  When he spoke, he almost wished the words would bring the tears.  His voice was tight as he said, ``I'd rather die in a blaze of glory than go out ingloriously.  I just-  It feels like it's something I need to do.  I can't put my finger on why.''



``We need you, David.  We can't lose you, gloriously or otherwise.''



``I know.''



``You're still among the strongest.  Only those who've watched from the beginning would know you're not at full strength.  There's some time before the changes become so pronounced the public notices.''



``They've already noticed.  The problem of being in the public eye.  Everyone's watching as I fail.''



She had no response to that, and he didn't volunteer anything further.  Staring down at the floor, he could see Contessa's legs in his peripheral vision.  She was leaning against the wall, watching.



He'd come to see her as a fixture.  Harder, now.  She couldn't give him the answer he wanted.  For better or worse, he was another of her blind spots.



The desk slowly slid back into place.  The Custodian was nowhere nearby, but she could move the furniture.



It made faint scraping sounds as it crossed the room, before it stopped in front of the Doctor.  The dust on the surface was whisked away in a swirl.



``You understand that this is necessary?''  the Doctor asked, the instant the dust was gone.



David nodded slowly.



``I'm going to go check on the latest recruits.  Let me know if you need to talk, or if you have any questions.''



He nodded again.



She stood from her chair, pushed it in beneath her desk, and then stepped out of the room.



His eyes followed Contessa as she stepped away from the wall and followed the Doctor out.



She hadn't said a word, but she usually didn't.  It had taken him some time to understand why.



Had the Doctor chosen, Contessa could have handled the entire discussion.  She would have won the argument.  Had she so chosen, she could well have framed it so that he walked away happy, content with the situation.



Yes, he was a blind spot for her, but she knew him well enough to construct a sufficiently `David-like' model in her head, to come up with the right answers for every question and statement.  But he would have known.  He knew what she did and how she operated, and it would have colored everything.



With the blind spot surrounding him, she couldn't refine her path to victory enough that she could make him walk away happy and content with the situation, to the point that he \emph{stayed }happy, stayed oblivious to what she'd done.



So he would come to resent her.



Doctor Mother handled the talking, instead, whenever she talked to anyone who she thought she might work with.  She took no overt cues from Contessa.



Every time Contessa was silent, she was holding back.  A weapon, held in reserve, an answer to every dilemma, from the most trivial to the most major.



She brimmed with \emph{potential} power.



It was uncharitable, Eidolon knew, but he resented her a little for it.



For all of his loyalty, his devotion to the mission, he found it ominous, in a way he couldn't place.



Staggering a little, as if he were wounded, he made his way to a standing position.



\emph{Obeying, being a good soldier.  Acknowledging the greater good.}



\blacksquare



\strong{June 24th, 2013, now}



Glaistig Uaine caught him.  He had the ability to fly.



His other power was manifesting.  His skin prickled, and that prickling soon extended to his costume.  In moments, he could feel it as an extension of himself.



His vision changed, shifting to an aquamarine color as the pane of his helmet took on another texture.  Crystalline.



The crystal continued to grow, forming more layers of crystalline cloth, ornamentation and more.



Something that would withstand a broad attack that his other defensive ability couldn't dodge.



He exhaled slowly.



``Thank you,''



``I am glad to be of assistance, High Priest.''



He stared out at the horizon.  There was a golden light at the edge, and it wasn't the sun.  Scion, approaching with a surprising deliberateness.



``\emph{Testing.  Testing}.''  It was a young woman.



``I'm here, Tattletale,'' he spoke, letting his power alter his voice.



``\emph{Lines went dead.  We just got camera and audio}.''



``You're going to lose it again soon.  He's coming back.''



\emph{``The test is done.  It went about as bad as we could have hoped against, but it's done.  There's no need to fight}.''



Eidolon thought back to that conversation he'd had with Doctor Mother, six months ago.



\emph{Going out in a blaze of glory}.



``I have more things to try.  I'm reasonably confident I can survive.  Glaistig Uaine is here too, but I don't know how committed she is to the fight.''



``You're talking to the negotiator,'' Glaistig Uaine observed.  Eidolon nodded.



``\emph{Whoops.  My bad.  I do not get this system at all.  Got you on the line, magnificent Faerie Queen.}''



Glaistig Uaine nodded once, confirming.



``\emph{We're not going to second guess you two.  If you think you can try some stuff that might maybe possibly theoretically work, I'm thrilled.  We're reeling.  Lots of dead, morale's rock bottom.  Just going by what I'm getting from my power, more than half the people who were on board before this are running scared.  You want to buy us time?  I'm not complaining}.''



The light was fast approaching.



``\emph{I'm guessing we're going to go dead.  If you guys want to kick some ass, put on a show, it'd do a hell of a lot for people's confidence, keep more soldiers on the battlefield. We've got a lot of ground troops who wouldn't have been so good in this last test run, Lung and a few others.  If you do well here, might mean we can keep them from changing their minds, yeah?}''



Eidolon could feel his power shift in response.  Same power, but different application.  ``Perhaps something more dramatic, if the opportunity allows?''



\emph{``Make it dramatic enough that they can see from a distance, or stay alive so we can get the logs off the cameras you're wearing.''}



``I'll try to oblige,'' Eidolon said, his voice dry.  His eyes were fixed on the growing golden light.  His power was already obliging, had been before he asked the question.



``\emph{The-}''



The line went dead.



A moment later, Scion attacked.  A flash of light.



The light penetrated the bubble, and Eidolon was gone, a quarter-mile away.



Reactive teleporting.  He felt the bubble form around him.



Eidolon focused on Glaistig Uaine.  She responded by creating a spirit that formed a construct of metal, like a dragon the size of a small island flowing from a point the size of a grapefruit.



The metal construct grew faster than the laser tore through it.  It slammed into Scion.



He physically tore through it, and Glaistig Uaine maintained the assault until the last second, before teleporting to join Eidolon once more.



Still cloaked in the shifting garments, Glaistig Uaine was breathing just a little harder.



``Just you and me left,'' he commented.



``No, High Priest,'' she said.  She composed herself.  ``There are others.''



``Others?''



``The wounded, who could not walk through the portal of their own will.  Some down there.  A meager few.''



``I see.''



Glaistig Uaine formed her garments into a shell around her.  Eidolon followed suit, drawing his arms in front of his face.



``And there are the dead as well,'' the Faerie Queen's voice echoed from within her cocoon.  ``We mustn't forget the dead, High Priest.''



Eidolon thought of Alexandria.



Scion struck.  An indistinct attack, striking everything he could see at once.



Eidolon reeled, flying through the air, momentarily berift of his flight.  The remains of the structure toppled before he even reached the apex of his trajectory.



Glaistig Uaine caught him once again.



The explosion had afforded Scion a chance to close the distance.  It would be harder to dodge, harder to time defenses.



Eidolon, for just a moment, imagined he could sense Scion's \emph{distaste}.  The Faerie Queen was between the two of them, but Scion ignored her in favor of \emph{him}.



Eidolon used his matter creation power.  As with the Faerie Queen's monster of steel, this was derived from a single point, an expanding creation of matter.  In this case, however, it was an \emph{explosion}.  Carbon unfolded from a single point.  Eidolon chose Scion's right ear canal as the center point.



The carbon expanded as a sphere, and there was a glimmer of Scion's reaction as the orb expanded until it was a hundred feet across.  A distortion, golden flesh stretching.



Blood?



The sphere dropped towards the ocean like a comically large cannonball, and Scion advanced.  Intact, unhurt.



\emph{Does he heal, or was my mind playing tricks on me}?



Scion lashed out, fifty-foot blades of golden light extending from his wrists, and the bubble was once again penetrated.  Eidolon teleported a distance away.



His pulse was pounding, his attention focused.



\emph{This is my focus, this is what I'm here for}, he thought.



A repetition of the last attack.  A charge, another laser prepped.



He moved to create the same sphere of carbon.  A crevice was best.  Scion's mouth was closed, but his nose-



Eidolon didn't choreograph his attack, didn't move his hand, didn't act, but he placed the next sphere of carbon in Scion's left nostril.



Scion shifted direction at the last second.



\emph{He's adapting, learning}.



\emph{Smug, superior}.  The feelings mingled with the faint sense of disgust that Scion seemed to radiate.  \emph{Confident.  Amused.}



Another attempt, another miss.  Scion's reaction was faster.



The bubble was breached by a narrow golden beam, and Eidolon reactively teleported again.



Scion followed up with a blast of golden light, again, radiating in every direction.



The bubble hadn't reformed, and it wasn't strong enough.  Eidolon's crystal exterior cracked and wore away.  The attack wasn't letting up, the crystal wearing down.



He could drop a power, but which?  To lose the crystal exterior would end his life before another power was on board.  The teleportation?  He'd be a sitting duck.  Losing the offense, when it was something that almost worked, no.



He held tight to each of them, grit his teeth as the light dug into flesh.



He felt his flight leave him.  An effect of the golden light?



No.  Something else had caught him.



Scion let up, leaving Eidolon to desperately cast aside the crystal exterior and pray for regeneration.



His flesh began to heal, forming bone ridges where flesh met flesh.  It would take him some time before the bone fell off, but it was the fastest regeneration he had available.



A trio of objects moved towards the alien from the fallen rig.  Spheres.



They detonated, each one exploding a fraction of a second after the one before.



Glaistig Uaine.  She had four spirits with her, and three were working in concert. One to form raw materials, two to fashion them into objects, a telekinetic to manage it all by holding Eidolon immobile in the sky while launching the bombs in Scion's direction.



One bomb was creating spaces of alternately accelerated and decelerated time.  Another was distorting space to the point it was painful to look at.



Eidolon banished his powers, keeping only the offensive one.  Could he afford to draw Scion's attention?



No.



But he did anyways.  He focused on the other ear canal.



Scion shifted to one side, whirling around to face Eidolon.



\emph{I'm not strong enough}.



\blacksquare



\strong{June 21st, 2011, two years ago}



They gathered where they had met innumerable times in the past, but they were quiet.  There was no confidence, no assurance.



Legend stayed by the door, not taking a seat at the table.



``Bound to happen eventually,'' the Number Man spoke.  ``The odds-``



``Don't,'' Alexandria said.



The Number Man shut his mouth, turning his attention to his laptop.



Eidolon pulled off his mask, brushed at it to clean it of the slime from when he'd been swallowed and then vomited back up.



He stared down at the opaque pane.



``We'll need to think,'' Doctor Mother said.  ``What does this impact?  The next Endbringer attack, at the very least.  We can't afford to lose a fight at this juncture.''



``The Protectorate,'' Alexandria said.  ``We'll lose members.  Critical members, no less.  We'll retain others, but the tone of things will change.  I'll need to step down, but I can effect some change before I do.''



``It changes a great deal,'' Legend said.  ``Forgive me for asking, but are you \emph{sorry}?''



``Not in the slightest,'' the Doctor said.  ``What we've done, it's always been with a singular goal in mind.  We knew it would be ugly, but-``



``You created the Siberian,'' Legend said.  ``The Siberian killed Hero.  Every action has effects.  Stupid, \emph{mindless} arrogance, and look at what it cost you.  Hero's death spelled the end of our best years, countless members of the Wards and Protectorate were disillusioned.''



``One could argue,'' the Number Man said, ``that his death spurred others forward.  He was a martyr.''



``I'm sure he'd be comforted by that argument,'' Legend said.  His voice was hard.  Days of pent-up anger were now being given a voice.  ``You told us this would be a net gain for the good in the world, more heroes.''



``It has,'' the Number Man said.  ``Less than we hoped, but a net gain nonetheless.''



``\emph{Gray Boy}?  \emph{Siberian}?  \emph{Human experimentation}?''



``Yes to all of the above,'' Doctor Mother said.  ``I won't lie to you at this juncture.''



``I'd ask to see this testing facility, but I'm not sure my conscience could withstand it,'' Legend said.  ``My god.  What have I done?''



``You unknowingly participated in our greater scheme,'' the Doctor spoke.  ``If it's any consolation, your conscience was strong enough that there wasn't a good way to bring you fully on board.  Whether we're branded as the heroes or the villains of history will depend on the outcome of this war.''



``I'm not sure I can believe that,'' Legend said.  He ran his hands through his wavy brown hair.  Beads of sweat stuck to the strands.  ``I have to go \emph{home}.  Look my husband and child in the eyes.  Are they- will they \emph{know?}``



Contessa spoke, stepping forward.  ``Alexandria handled the situation masterfully.  We can curtail this information with some swift action and discouragement.  A few weeks of activity and people will stop trying so eagerly to spread the word.''



Legend stared at her, uncomprehending.  When he spoke, his voice was level, out of alignment with his expression, his narrowing eyes.  ``Two questions.''



``Please,'' she responded.



``First of all, who the fuck are you, to decide?  You'd go after heroes who'd want to spread the word, why?  To try and silence them?''



``I would succeed.''



He shook his head.  ``And my second question\ldots who the fuck \emph{are} you?  All this time, you've been lurking around the Doctor.  You're more than just a bodyguard.''



``I'm the person who would succeed,'' she said.  She glanced at the Doctor.  ``At whatever she needs me to do.''



Legend shook his head again.  ``You're all so cavalier about this, so mechanical.  It means nothing to you?''



``It means a great deal,'' Alexandria said.  ``We lost a great deal of power, leverage, trust.  The heroic organizations are going to be sundered by this knowledge.  Try as we might, we can't erase their memories.''



``No,'' Doctor Mother said.



``Unless you wanted to use the slug?''  Alexandria mused.



Doctor Mother shook her head.



``The slug,'' Legend spoke.  ``I was wondering how the case fifty-threes came to lose their memories.  Not something of Manton's, because he wasn't involved in making them.  It's yours.''



``It and others,'' the Doctor said.



``Aren't you \emph{ashamed}?'' Legend asked, his voice rising.



``I'm ashamed,'' Eidolon murmured.



Heads turned.



``I failed.  On many levels.  We lost this fight.''



``We've lost before,'' Alexandria spoke.



Eidolon looked up at her.  ``Can you look at me and tell me we wouldn't have won this, years ago?  When I was new to the game?''



She met his eyes.



He let go of all of the powers he held, waited for others to take root.  ``I'll know if you lie to me.  You can control your body language, but I'll know.''



She lowered her gaze.



``Yes.  I'm getting weaker.  We're slowly approaching the moments where we need to be strongest, the most critical battles, where any one Endbringer attack could mean a chain reaction of loses, the world being too weak at the end\ldots and I'm getting weaker.''



``And you worry you'll be too weak to contribute in the final days,'' Alexandria said.



``Yes.''



``Final days?'' Legend asked.



``We know who ends the world,'' Alexandria said.  She met her old leader's eyes.  ``We know \emph{what} ends the world.  Scion.''



Legend's eyes widened.  ``And you haven't told anyone?''



``It would be disastrous,'' Doctor Mother said.  ``Disastrous and premature.  Especially \emph{now}, with morale already critically low.  We'd hoped to wait, to time things.  Everything we've done this far has lead to this eventuality, but we need all of the organizations across the world on board, we need assets, ones we've developed thus far and ones we're going to work on shortly, and\ldots we need Eidolon.''



Legend glanced at him.  ``For his strength?''



``He's an anomaly.  We can only guess, but he's an outside case.  A deviant case that isn't deviant in anything but execution.  He breaks rules, and that's something we can use against the enemy who decided the rules this game would be played by.''



``But I'm weaker,'' Eidolon said.  ``Too weak. My powers are slower to arrive.  I use one power too much, and I lose it.  I can't tap it again.  I can't \emph{choose} what powers I get, so my agent reaches for those which serve double uses, and when they get spent, I'm left less versatile.  Even then, the powers aren't quite what they were.  Fire doesn't burn as hot, lasers aren't as focused, ranges aren't as great.  If I couldn't beat Echidna-''



``Then we have to find others.  More experimentation,'' Doctor Mother said.  ``We'll have to hope for another Eidolon.''



Eidolon set his lips in a grim line.



``More experimentation,'' Legend said, stunned.



``Contessa will explain,'' the Doctor said.  ``If you're willing to hear her out?''



Legend hesitated.



``Fine,'' he said.



\emph{Being replaced,} Eidolon thought, \emph{a tool to be used by others.  I agreed to it, but\ldots}



\blacksquare



Scion cast out another shaft of golden light, and Eidolon was flung across the sky by Glaistig Uaine, his powers still taking hold.



\emph{Not strong enough}.



He created more matter.  Scion avoided it for the third time.



Despite Eidolon's desires, the matter-generation power began to recede.  His agent had apparently decided it wasn't sufficient.



It hurt Scion once, hadn't it?  Or had he wanted it to so badly he'd seen it?



He began to glow, a brilliant azure.



Eidolon took on the form of a living field of distorted space.  Air ignited on contact with him.



Scion lashed out, and he danced around the edges of the blast, closing the distance to swamp Scion.



There were abrasions where Legend's finest lasers had cut.  He drove his new body into them, expanded.



It was working.



Up until Scion radiated golden light.  Nine tenths of Eidolon's body was destroyed.  The remainder was cast out across the sky.



Too far apart to pull himself together.



The Faerie Queen did it instead, using the long-ranged telekinesis, bundling him together.



His senses became a haze as he traveled, indistinct and incorporeal.  He found other powers, and he painstakingly rematerialized.



He was beside Glaistig Uaine, and the world around them was gray, shrouded in thick mist.  Scion's beam pummeled some unseen barrier.



``A reprieve,'' Glaistig Uaine spoke.  ``I thought you'd need one.''



``You're more powerful than I am,'' he said.  The words broke him a little.



She shook her head.



``No?'' he asked.  ``Or is this a faerie riddle?  It's not really \emph{your} power?''



``It's mine.  Ours.  But you're stronger than I am.  I can see it.  The issue, High Priest, is that you need to open your eyes.''



``My issue is that the well has run dry.  I can't tap it for power anymore.  My best abilities are gone, and I'm spending the remainder with every minute I fight.''



``Refill the well, then,'' she said.



``It's not so simple, but I'll take any suggestions.''



``I've given it to you several times.  I'll tell you again, open your eyes, High Priest.  You weren't given your role on purpose.  You \emph{took} it, understand?  Now you need to wrap your head around your duties.''



``What \emph{are} my duties?''



``Those of the High Priest.''



He almost swore out loud.  ``Less riddles, more answers, please.  Unless you're interested in dying here.''



``Death is inevitable.  Life is too.  Even if Scion succeeds, there will be some who remain, because they hid well enough, because they aren't interesting or different enough to kill.  Life, death, a binary.''



``This isn't constructive.''



``It can be, but I won't repeat myself a third time.  Binaries.  Everything represented on the other side of the mirror.  Not perfect reflections, but reflections nonetheless.\emph{``}



``What's my reflection, then?''



``You should know,'' she said.



``\emph{You}?''



``Mm.  No.  But I could be, in a small way.  Like I said, the reflections are distorted.''



``Your power is death, my power is life?''



``Not so overt, but you're thinking along the right lines.  I am alive as the faerie queen, I collect the dead, I tap them for my strength, to better shepherd them.  You are the High Priest of the stillborn faerie, but you could tap the living for strength.''



``\emph{How}?''



Glaistig Uaine pursed her lips.  ``I told you twice and alluded to it a third time.  I do like \emph{threes }as numbers go.  There's a significance in threes.  Triads, \emph{triumvirates}\ldots''



He thought back.  ``Open my eyes.''



``Yes.  I was starting to worry you'd injured your head in the fighting.  I would hurry.  The next demonstration will occur soon.''



\emph{Open my eyes}.



His powers were defensive and offensive ones.  Possibilities, still growing to full strength.



Scion was knocking down the barrier.  To relinquish those defenses in the face of Scion's imminent attack\ldots



He did it, cast them all aside.



A leap of faith was nothing if he didn't take it with nothing held back.



He felt powers stirring, manifesting.  Three powers lost, he could only hope that one of the three new powers would be sufficient.



He prayed.



\emph{God, let me see.  The agent never listens, but please, for all that is right and just in the world, let it give me the ability to see}.



He felt the powers begin to take hold.



Something affecting his body.  He cast it aside.



The barrier around them flickered.  For an instant, the water and the sky around them were blue.



Another power, something offensive, in his fingertips.  He banished it.



Flight, the ability to run.  No.



Six powers lost and gained.



He'd dug deep while fighting Endbringers, while fighting Echidna, the Blasphemies, and other great threats, but it had been for something offensive.  Something safe in its own way.



To dig so deep for something mental, it was scary.



Something he'd explored, but not like this.



He took a deep breath, murmured an indistinct prayer, and tried to empty his mind of all of the other needs and wishes and fears.



With the seventh power, he felt a sensory change.



He could see the passengers light up, taking form.  Glimmers of images, shadows, scenes both Earthly and alien.



Glaistig Uaine was a mosaic, a stained glass window of three interlocking scenes, flowing into and through one another.  Three spirits.



He could see how she reached out to them, how they flowed into and through her.



This was \emph{her}.



What was \emph{he}?  What was his dream?



``\emph{Now},'' she said, as if from very far away.



Nearby, a cape who had been wounded in the rig's collapse died.  He could see the images start to fade, to degrade, consumed from the edges like darkness might creep in around one's peripheral vision as they lost consciousness.



He saw Glaistig Uaine claim them, banishing her creations and leaving only the framework around the images.



The framework took in the other cape, and it bloomed with a new life.



He felt his own power stir.



It emulated, copied.  Grasping tendrils, reaching for Glaistig Uaine.



He saw her expression change, repressed anger.



No.



\emph{The living}.



There weren't many.  Four that had been left behind, for whatever reason.



He used hydrokinesis to bring them closer.



The tendrils connected to the images surrounding them, abstract ideas, as though the agents had no identity or concept of their own beyond the memories they stored.



He felt his power grow, hurried to allow new powers to fall into place so he could fill them with reserves, tap them for energy.  Tendrils connecting agents here and elsewhere.



They'd lose their abilities, be rendered weaker.  They were dying anyways.



New powers fell quickly into place.  They reached a greater capacity in less time.



Still standing at the edge of the ruined platform, Eidolon's took in a deep breath for what felt like the first time in a \emph{decade}.  A weight had fallen from his shoulders.



Two powers, a third for this extra perception, the ability to tap others for energy.



He tapped into an erasure power he hadn't had since he had fought Behemoth the first time.  Destroying matter.  No defense to penetrate, nothing to attack or avoid.  Merely a vast area cut away.



Scion moved, but the affected area was as broad as a tennis court.  The golden man lost a hand.



Thunder crashed as air rushed in to fill a space where even the oxygen molecules had been cut away.



\emph{Something to keep him still.}



Another power was needed.



The power was a familiar one.  One he'd used to curtail Leviathan's movements in the Kyushu fight.  He reached into another Earth and pulled the cliff faces into this world.



Scion blasted the cliff faces, but his golden light only affected the cliff on \emph{this} earth.  The moment he stopped, more emerged.



He stopped to strike again, this time obliterating the cliff faces on \emph{this} Earth and the one in the other reality.



Eidolon struck out with the erasure power while Scion was still.



Thunder clapped.



Scion was gone.



No.  Not gone.  He had slipped into another Earth, avoiding the affected area as easily as someone might avoid a thrown stone by stepping to the right.



Glaistig Uaine approached Eidolon.  She granted him the ability to fly.



He banished one power, felt another come back to him.  He fed off two more of the injured capes.



He used the new power to shove himself and Glaistig Uaine into the next reality.  He fixed his eyes on Scion, then lashed out, shoving \emph{part} of the golden man into one reality.  Scion reeled, then retaliated.



Glaistig Uaine created an obstruction, the tornado-mass of swirling blades and iron that emerged fast enough to absorb the beam's impact.



Eidolon slashed with another reality \emph{push, }and Scion disappeared.



Running.



\emph{Nearly as strong as I was in the beginning}.



He nearly felt like \emph{himself}.



\blacksquare



\strong{May 1986, }\strong{twenty-seven years}\strong{ago}



\emph{A strange place for this discussion}.



The woman looked supremely at ease as she took a seat opposite David.  The teenage girl who accompanied her was just as confident.  Here and there in the little cafe, people gave them dirty looks.



The woman was black, dressed all in white, the girl wore a private school uniform and held a notebook and fountain pen.



They were tidy, prim.  David felt underdressed, \emph{small}.



``I admit to being a little confused,'' David said.



``Understandable.  You can call me Doctor.''



``No last name?''



``No need.''



He frowned.



``What do you think?'' she asked.



``I'm kind of bothered by the lack of a last name,'' he said, ``If you'll pardon my saying so.''



``Pardon granted,'' the Doctor said, smiling slightly.  ``Very polite.''



David frowned a little at that.  ``Somehow, I get the feeling you know everything about me, and I don't know anything about you.''



``At this stage, very likely.  But I'd still like to talk as if I \emph{didn't} know all of the details.  You applied to the army, and you were turned down.''



David chewed his lip, looking across the cafe.  It wasn't a big town.  How many of his father's friends or acquaintances were here, possibly listening in?



``You aren't surprised, but\ldots you were still clearly disappointed, crushed.''



``Don't,'' he said.  He stared down at the table, his lips pressed into a firm line.



``They aren't listening, not really.  They're busier looking at a black woman in a town where black women are rare,'' the Doctor said.



``Sorry,'' David said, suddenly feeling embarrassed.



``Your town isn't under your control.  What \emph{is} under your control is what happened last week.''



David clenched his jaw.  Lines stood out on his throat as he looked out the window.



``You tried to take your life.  The army, it was something you wanted?''



``I just- I know I'm not in any condition to fight, to do drills or any of that.  But there's other stuff I can do.  Desk jobs.''



She nodded.  ``I can offer you better than a desk job.''



``Part of me thinks you stole a look at my records,'' he said.  ``And now you're here to make fun of me.''



``I don't intend to make jokes at your expense, David.  What does the other part of you think, if not that I'm an unscrupulous medical doctor with a bad sense of humor?''



``That if you told me your name, it'd be something sinister.  Fire and brimstone.  This sounds an awful lot like a deal with the devil.''



``I suppose it does.  I'm only mortal, I confess.''



David frowned.



``I can't make promises, David.  Infernal, divine or otherwise.  I can't tell you that you'd be joining the army.  Just the opposite.  It would raise a number of questions.''



He glanced out the window again.  He felt so ashamed of himself he couldn't meet her eyes.  ``The army wasn't the thing.''



``No?''



``I wanted to go do something of my own will.  Take charge, take \emph{action}.  Stop living a life where everything is decided for me.''



``By joining the \emph{army}?'' the Doctor raised an eyebrow.



He laughed a little.  ``I know.  Stupid.''



``You wanted independence.  I can't promise it.  In fact, if this deal with the devil goes through, it might be something I demand from you.  Your assistance, your aid.  I need a \emph{soldier}.''



He took his time thinking about it.



``I've thought it over, I get that there would be obligations.  Yes.  Please.  I'll do it.''



``I did outline the risks?  The chances are slim at best.''



``Yes.  Well, I obviously don't put much stake in my own life, do I?''



``Apparently not.  Good, come,'' she said.  ``We'll do this now.''



He nodded.



His hands were stiff to move as he brought them to his sides and unlocked the wheelchair's wheels.  The scars on his wrists were only part of it.  The nerve damage from the seizures he'd had several times a day since birth were the rest.



He avoided the eyes of the people around him as the Doctor took hold of the wheelchair's handles, guiding him to his destination.



\blacksquare



\strong{June 24th, 2013, now}



He was catching up.  Scion continued to run.



A world without air.  He held his breath.



A world of magma and smoke.  Glaistig Uaine provided the protective shield.



More and more remote Earths, less habitable, less familiar.  Earth Bet was a long, long way behind them.



A glimpse here, of Scion with his back turned.  A glimpse of Scion, hand raised to attack.



Eidolon counterattacked with a distortion in space, while Glaistig Uaine provided a defense, moving them a distance away.



``Almost,'' he said.



``Almost,'' she said.



He remembered Weavers warning.  He couldn't trust this girl.



But he had to.



Every step of the way, his life had been decided for him.  He'd been the disabled kid, carted everywhere by his mother and father, barely able to wipe his own ass.  Careers denied him.  Superheroics chosen for him.  Then predestined events, the dissolution of his career in the triumvirate, the looming end of the world.



This was the closest he'd ever felt to being free, but still, there were obligations.  He had a mission, he knew what to do.



Another attack.  Glaistig Uaine coordinated with him on this one.  Another attack, rending Scion.  An attack that would have killed an ordinary man.



He could sense a degree of distress.  Of \emph{concern}.  Not as dramatic as the disgust he'd felt from Scion before, but noticeable.



If Glaistig Uaine was going to betray him, it would be now.



``Are you going to stab me in the back, Faerie Queen?''



``Every time-'' Glaistig Uaine spoke, stopping as they stepped into a lush Earth, ``\emph{he} uses his power, it costs him time.''



``Time.''



``He experiments, he plays, but he doesn't yet abandon hope.  \emph{I} don't abandon hope.  The cycle could yet complete, by luck alone.  He needs to find his reflection in the mirror.  He lost his, like Peter lost his shadow, but another could appear.''



``This doesn't answer my question.''



``You are so blind, High Priest.  Deaf.  He will not let himself run out of time.  If he runs out, then he will stop playing, stop experimenting, and simply \emph{wait}, bide his time in the hopes that another will come to act as his reflection.''



``That's your goal?''



``It is.''



\emph{I believe you}.



He redoubled his efforts, no longer worried about defending against a possible attack from just to his right.  They passed from world to world as quickly as he could make portals between them.  They drew closer\ldots closer still.



And came face to face with Scion, mere inches in front of them.



He'd stopped, turned around.



Glaistig Uaine distanced herself from Eidolon, until she was to Scion's left.  Her body was tense, ready for an attack.  Eidolon raised his hand, ready to attack.



Had Scion decided on a tactic that would cost him less time than he was losing by taking Eidolon's repeated attacks?



He had.



Scion spoke for the second time.



Four words, barely audible.



It took time to sink in.



Eidolon let his hand drop to his side.



He turned the sounds around in his head, trying to convince himself of a different configuration, convince himself he had heard wrong.



But he hadn't.\emph{  }It dawned on Eidolon. \emph{ He has Contessa's power}.



\emph{How many years did it cost Scion to use it}?



Not enough, he was convinced.  Scion had defeated him.



Scion raised a hand, and Eidolon didn't move.  Glaistig Uaine was fleeing.



Scion fired the lethal blast.





