





``Francis!'' The word was an admonishment.  ``Where do you think you're going with that?''



He hung his head.  The luggage he was hauling behind him was on wheels, but he propped it up so it stood straight, sticking his hands into his coat pockets.  He reluctantly turned to face his mother.



``We have family over.  Your Uncle Felix came all the way from California.  I think they \emph{might} want to spend some time with you this Christmas.''



``You arranged that.  I made these plans \emph{weeks} ago, I told you about them.''



``Nothing that involved luggage,'' she folded her arms.  Olive skinned, with a hawkish expression, his mother managed to look intimidating even though she was an inch shorter than him.



He bent down and placed the luggage flat on the ground.  He unzipped it and opened it for her to see.



She sighed.  ``It's not a productive pastime.''



``I'd say it's pretty productive.  We stand to make a pretty decent amount, here.''



``You're going to make money?''



``We already are.  But the thing is, depending on how today goes, we could make a lot more.''



``You're dissembling, Francis.''



He cringed, more at hearing his name than in response to the accusation.  ``I was going to save it for an announcement in front of the family tonight, after we see how it goes.  We have stuff to hash out first, and it probably won't be pretty.''



She gestured for him to go on.



He frowned.  ``We're on the verge of getting a sponsorship. It's pretty generous, too, even split between the five members of the team.  And it's in addition to what we already make.  Contract's just for one year, and if we prove ourselves, show we can hold our own, we could get a bigger, better contract when we renew the terms next year.''



``This sounds a little too good to be true.''



``We're good, mom.  \emph{Ridiculously} good.  The sponsors have been talking about us being on the international stage.''



``And just who is us?''



``This is starting to feel like an interrogation.''



``It should.  Who's on the team?''



``Well, there's two answers to that question-''



``Francis,'' she made it sound like a warning.



``You don't know all of them.''



``Mm hmm.  Is your alleged girlfriend in this group?''



He nodded.  ``Yeah.  Her, Ms. Newland's daughter-''



``Oh, lovely.''



``No, she's cool.  Then there's this girl named Jess, there's Cody, and Luke.''



``You left yourself out.''



He smiled sheepishly.



``You're not in the group.''



``Yet.  Like I said, we have stuff to hash out,'' he said.  He tried to force the smile from his face and failed.



``It's dangerous to mix business and friendship.''



``I'm being careful.''



She gave him a sharp look.



``Really!''



``Go.  Be back by two.''



``Can't.  Going to take all day.  I'll be back seven-thirty-ish.''



``Seven.  If you're late for dinner I'm taking your biggest present back to the store for a refund.''



``I don't know how long it'll take.  I can't make any promises, and all of this is kind of important to me.''



``Then decide if it's worth losing the present.''



He rolled his eyes.  ``I guess it is.  Love you, mom.''



``Go.  Get lost.''  She smiled as she said it.



He zipped up his luggage and headed outside.



It was crisp.  Fat snowflakes drifted down from above.  He tugged his scarf tighter and headed out, the bottom edge of the luggage wiping out his footprints behind him, the wheels serving as the only trace of his passing.



His breath fogged up in the air, making his scarf damp around his mouth.  This moisture, in turn, froze, making the fabric of his scarf stiff.



It wasn't a short walk to the bus stop, and getting the luggage onto the bus was a chore.  It didn't help that it was crowded, packed with men, women and children eager to finish their Christmas shopping.  He should have felt bad about the awkwardness of having his luggage there, getting in people's way as they got on the bus, but he didn't.  A part of him thrived on being annoying.  He liked to think it nourished him.



He even felt a little smug.  He'd finished his shopping in September.  Half of his motivation had been to avoid the hassle.  Half was so he could lord it over friends and family.



Getting off the bus with his luggage was twice as hard as getting on.  He made his way into the coffee shop and scanned the crowd.



He saw her, but he didn't hurry to her side.  Instead, he spent a moment standing by the door, watching as she stood at the end of the short line.  Her cheeks were red from the cold, and the snowflakes had melted into droplets on her eyelashes.  Some flakes still clung persistently to her straight brown hair.  She made her way to the front, and ordered.  While she waited, she dabbed at the snow, wiping her eyes and hair, and then tucked her hat into her pocket.



Seeing her rub her cheeks to warm them, he felt an urge to hold her as tight as she could bear, to feel her cold cheek against his, to warm her with his body, and to let her warm him in turn.  It caught him off guard in its suddenness and intensity.



He took a deep breath and crossed the coffee shop to wait by the far end of the counter.  He jammed one hand in his pocket, as if that could keep him from following through on the impulse.  After a few seconds, he pulled it out again.  He \emph{did} have self control.



Her face lit up as she saw him.  He, in turn, snapped a smart salute.  ``Captain Noelle, ma'am!''



``Don't!''  She blushed.  ``People are going to stare.''



``I don't mind.''



``I do!''



He smiled and led the way to the nearest empty table.  He used one foot to slide the luggage bag against the wall and then pulled her chair out for her.



``I can't tell if you're being a gentleman or if you're trying to sweeten me up for this talk of ours.''



``I'll take that as a good thing.  It means I still get the brownie points, but you won't be hard on me to make up for the fact that I'm being conniving.''



``I \emph{should}.''



``Besides, it's my prerogative to treat you well, right?''



She smiled a little and took another sip of coffee.



``We \emph{are} boyfriend and girlfriend?'' he asked.  He could see the smile fall from her face.  He hurried to speak before she could protest.  ``Probationary boyfriend and girlfriend.  You know you can still break this off any time, right?  Don't give a second thought to my feelings.''



``That's not it.  I like you, Krouse.''



Francis Krouse felt something jolt inside him.  It was like surprise but not.  He already knew she liked him, but hearing it said\ldots  he felt his face warming up, and distracted himself by untucking and folding his scarf.



Finding himself unable to look directly at her, as embarrassed at his own embarrassment as anything else, he replied, ``I like you too.''



``I just- I worry I'm not being fair.  We don't actually-''



``We do what we want to do, right?  We enjoy each other's company?''



``Yeah.''  She sipped at her coffee again, then put it down to rub her hands for a second.  ``I enjoy your company.''



Tentatively, he reached out and placed his hand over hers.  Cold.  He reached out with his other hand and placed it under hers to help warm it.



``Look at this.  Krouse is being sweet,'' a girl said.



He turned in his seat to see the others.  Marissa wore a pristine white jacket with a fur ruff.  Between her delicate features and the way her blond hair glittered with the moisture of the snow, she looked almost angelic.



Luke was almost the opposite.  Grungy, mismatched, dressed in layers, with a plaid green button-up shirt under a blue jacket, and a red t-shirt beneath that.  His beard was a thin teenage scruff.  He bumped fists with Krouse before sitting down.  Krouse was almost embarrassed to realize he was doing something so stereotypically `cool'.  It had started as something they did ironically and turned into habit.



Jess was the last to join them, navigating between the chairs, tables and other customers, making sharp turns as she wheeled herself to the table.  Her hair was shaggy, she had three piercings in one ear and thick eyeliner around her eyes.  A shopping bag sat in her lap and more were hooked over the handles of her wheelchair.



``I'm sorry, Jess,'' Noelle apologized the second the girl arrived.  ``We should have found a table closer to the door.''



``She keeps saying she doesn't want us to treat her different,'' Krouse said, shrugging.  ``Don't see why we should have.''



Jess gave him the finger.  ``There's a middle ground that lies between being an asshole and being so accommodating that you make me feel like a freak.  The others have found that middle ground, I don't see why you can't.''



``I'm doing exactly what you asked for and not treating you any different than I'd treat a non-cripple.''



``Alright, alright,'' Marissa said.  ``Let's not get into another argument.  We're short on time.''



Noelle nodded, ``We don't have long before we have to get ready, and we really should figure out what we're doing.  You guys got my emails?''



Marissa sighed, the mood changing in a flash.  ``Yeah.''



There were nods from the others.  Krouse stayed very still, watching them.



``This makes things complicated,'' Luke said.  ``You're in charge, though, so you get the final say.''



Noelle made a face.  ``I know, but the problem is we're not just teammates.  We're friends.  And you guys know that Krouse and I are dating.  That complicates things.  I don't think I have the perspective to make the call on my own.  I put my thoughts in the emails, I'm just hoping you guys can give me some direction.  If you say we shouldn't-''



``No.  The shitty thing is that the logic is sound,'' Luke said.  ``No offense, Krouse, but this would be a lot easier if you sucked and we could kick you to the curb.''



Krouse shrugged.



Luke went on, ``Look, if we were talking about staying local, being casual about this, or even sticking to the \emph{national} level, we'd keep Cody.  He's reliable, but he's not at the level we need if we're actually going \emph{inter}national.  He's boring, he doesn't have fans.  He won't get any future sponsors interested.  To top it off, he's too traditional.  He won't surprise our opponents.  They know how to deal with people like him.''



Noelle nodded.  ``Say what you will about Krouse, like how he's crap when it comes to calling shots-''



``Hey.''



``Or even the fact that he's prone to ignoring orders if he thinks it'll help us.  Um, he's right so long as it's just him operating solo, but yeah\ldots The thing is, if we're talking about the big picture, international recognition and going head to head with the best in the world\ldots Krouse has the natural ability to change things up, so we can adapt our strategies to whatever they're able to pull off.''



``And he has fans,'' Jess said.  ``As many as any two of us combined.''



Krouse couldn't help but smirk.



``As a call for the good of the team, it makes sense,'' Luke said.  ``But in terms of our friendships, well, Cody's going to be hurt.  He put in a lot of effort helping us get to this point.  He's my friend, just like Krouse is.  This is a pretty big betrayal, kicking the guy off the team right before we get our sponsorship.''



``Will the sponsor be okay with this?'' Jess asked.



``As long as we prove we're ready this afternoon,'' Noelle said.



``You know the arguments Cody's going to make,'' Marissa said.



``Yeah.''



``Can I say something?''  Krouse asked.



He could see them glancing at one another, trying to decide.



``So long as it's helpful,'' Jess replied.



``Look.  Cody is a type A personality.  Like Marissa-'' he saw Marissa's expression change and added, ``I don't mean that in a bad way.  Marissa and Cody are training the hardest and practicing the most.  That's respectable.  The difference is, well, we've all seen how much time Cody puts in.  And I think he's hit his ceiling, and he knows it.  He's not keeping up, and I don't know how much he's going to improve over the coming months or years.''



``And me?''  Marissa asked.



``I don't know how close you are to hitting the ceiling, but you have natural talent and ability that Cody doesn't.  I would have zero worries with you backing me up, even on the world stage.''



She pursed her lips.



``Anyways, we're talking about Cody.  He's not improving.  If I'm on the team, I'm going to work harder, I'm going to improve in every department, and I fully expect you guys to kick my ass to make me do it.  And I've been pretty excellent already.''



``If you fuck this up for us, you know we'll never let you live it down,'' Luke said.



``Of course.''



Luke sighed and said,  ``I'm caught between two friends, so I can only make this call in terms of the team and in terms of the business.  I think we should go with Krouse.  He'll put in the work, and we all know he's good.  Some practice and we'll get everything coordinated, and we'll be far stronger for it.''



There were nods all around.



Luke continued, ``Krouse was saying that Cody and Marissa are type A personalities.  He's not wrong.  Marissa's who she is because of the megabitch.''



Marissa frowned, but she didn't argue the point.



``And Cody's who he is because he can't stand to lose.  So how's he going to react if he finds out he's been bumped for Krouse?''



Nobody responded.  It was too easy to imagine.



``We're in agreement, then?'' Noelle asked.  She was hunched over her coffee, both hands wrapped around it for warmth.  She didn't look happy.  ``Last chance for objections, or to say if you're having second thoughts.  I won't be angry if you do.''



Did she want there to be a good argument against this, so there wouldn't be a confrontation?



Nobody spoke up.



``Let's go deliver the bad news then.''



While Krouse and Jess navigated their way past the maze of tables and chairs, Marissa hurried to the front counter and ordered.  She joined them outside a minute later, handing one donut to Noelle, who accepted it with a roll of her eyes.



They'd chosen the donut shop because it was only a block away from Luke's apartment.  It made for a short walk to their destination.



``Krouse, you want to take the elevator with Jess, rest of us will take the stairs?''  Noelle offered.  She turned to Luke, ``Cody here already?''



``Probably.  My brother said he'd stick around long enough to let him in before he went shopping.''



``So you want to break the news to him without me there,'' Krouse said.



Noelle and Luke nodded in unison.



``Alright,'' Krouse agreed.



``Krouse is being cooperative?''  Jess commented, quirking an eyebrow.  ``I'm impressed.  And a little unnerved.''



He smiled at that, and he looked to Noelle as he said, ``Good luck.''



A moment later, it was just him and Jess in the lobby, along with two elderly couples who were sitting in the chairs in the mini-lounge by the doors, talking.



``You must be nervous,'' Jess said.



``Never,'' he smirked.



``See, I have you figured out.  You have a tell, when you're lying.''



``Sure.''



``The more overconfident you act, the more nervous you are.  And when you're feeling down, you poke at people, provoke them.  I think you get some validation out of it, like, if you can test people and they're still your friends after, you can feel confident in that friendship.''



``Ohhh, seems like you spend a lot of time thinking about me.  Maybe a little bit of a crush there?  Eh?  Unrequited love?''



She broke into laughter, too sudden and hearty to be anything but genuine.



He shook his head a little and let her go first into the elevator before following with his luggage.



``What-'' he started speaking, but he stopped when she broke into another fit of giggles.  ``Come on, now.''



The thing was, he mused, Jess would probably be a good match for him.  She was probably the best when it came to keeping him in line, keeping him real, and calling him on his shit.  She wasn't bad looking either.



But she was in a wheelchair, and though he sort of wished he could be the kind of person who could take that in stride, he had to admit he wasn't.



Then there was Marissa, the most attractive member of their group by far.  Nobody would deny it.  Tall, blond, slim, with a body honed by years of dancing and ballet.  She was good looking enough that it was intimidating.  Odd as it was, nobody in the group had asked her out, as far as he knew.  Marissa's mother played a part in that; nobody wanted to deal with the megabitch.



Noelle, oddly enough, had been the girl they'd fought over the most.  It was odd because she didn't have Marissa's head-turning beauty or Jess's confidence.  It made her more approachable, in a strange way, up until the point where Noelle had shut down any and all advances.  Getting close to her had been a slow process, one with a lot of missteps on his part and skittishness on hers.



He had a sense of what the story was behind that.  Marissa knew too, by all indications, but he hadn't asked.  That was Noelle's private story, to be shared when she was ready.



The moment the elevator doors parted, he could hear the shouting.



``You assholes!  I didn't want him on the team in the first place and now you're \emph{replacing} me with him!?''



``Calm down, Cody.''  Luke, ever reasonable.  ``Shouting isn't going to help, and it'll bother the neighbors.''



``He's manipulating you!  He's a slimy creep, and you know this is \emph{exactly} why he's dating Noelle.  Or don't you find it a\emph{ little} suspect that they started dating almost right after we voted her captain?''



Krouse glanced at Jess, who furrowed her brow as she looked up at him.  They stepped out of the elevator and paused outside of the door to Luke's apartment.



Oliver and Chris were standing outside the door.  A more different pair was hard to imagine.  Chris was Marissa's friend.  After Marissa had dropped all of her old hobbies and joined the team, Chris was the only one of her friends who'd stuck around.  Krouse didn't see \emph{why}, but Chris tended to have girls all over him.  He was worlds different compared to Oliver, who was short, pear shaped, his blond hair cut in an unfortunate bowl-style that wouldn't have suited someone four years younger.



``You idiots!'' Cody swore.  ``You know he planned this.  Asshole thinks he's so smart, and you just feed that delusion!''



Chris mouthed the word `wow'.



``Cody,'' Noelle started, ``We talked it over-''



``Without me!''



``Because we knew you'd react like this, and we wanted to be sure we all agreed before we moved ahead.''



``And I bet Krouse was there, wasn't he?''



``He was.''



``Real fair.''



``He kept his mouth shut,'' Noelle said.



\emph{Not exactly true}, Krouse thought.



``He was still there.  You think the others are gonna say he sucks and he doesn't deserve a spot on the team while looking him in the eyes?''



It was Luke who answered him.  ``Honestly?  Yeah.  We would.''



The directness gave Cody pause.  Krouse decided to head inside.  He found Luke, Marissa and Noelle standing together against a red faced Cody.



``You.'' Cody narrowed his eyes.  ``You \emph{dick}.''



``I'm honestly sorry,'' Krouse said.  ``If there was a way for the deal to include all of us, I'd take it without question.  We can only have five.''



``But you have no problem stabbing me in the back for your own benefit.''



``It's more for everyone's benefit-''



``Except mine.''



``Really, I am sorry.  I know how hard you've worked.''



``I work twice as hard as anyone else,'' Cody stabbed a finger at Krouse, ``Ten times as hard as you.''



``And you're only about as good as Mars,'' Krouse said, shrugging, jerking his thumb in Marissa's direction.  ``And if I'm better than you while putting in as little effort as you say, how much better will I be when I'm\emph{ trying}?''



Cody clenched his fist, and Krouse could tell that he was about to swing.  He grit his teeth and braced himself for the hit.  Better to take it than-



``Cody,'' Luke cut in, putting himself between the two.  ``You're pissed.  You're allowed to be pissed.  I would be too, if I was in your shoes.''



``I thought we were friends,'' Cody replied.  The emotion in his voice was raw enough to make Krouse cringe.



``We are.  But this is business.  And we need to \emph{get} to business, because we only have a little time to get ready.  You can hit him, or you can stay.  Pick one.''



``Stay and watch him make his debut?''  Cody asked, bitter.



``This isn't set in stone yet.  If he fucks up today, if this doesn't work out-''



``We're boned,'' Cody finished.



``No.  We'll drop him and reinstate you, we'll apologize to our sponsors-to-be and we'll move ahead.''



``So I hit him or I stay and watch him crash and burn?''



``Basically.''



Cody smiled.  ``I'll stay.''



``Wonderful.''  Krouse smiled back.  ``We really should get ready.''



Everyone else was already set up, so they took on the job of prepping the room.  Luke shared his apartment with his brother and another roommate, but both had vacated for the day, leaving Luke the freedom to rearrange the furniture.  He recruited Marissa and Oliver to help with the moving of the stuff he hadn't been able to shift on his own.



Chris took the job of pulling the curtains closed, reducing the light that streamed in through the windows to a few glowing slivers that stretched across the floor.



Cody stood by with his arms folded.



``Here, Noelle,'' Krouse said.  He set his luggage flat on the ground and unzipped it.  There were computers inside, each half the size of a regular desktop, wrapped in layers of towels and plastic sheeting.



``Thanks for the loan.  Don't trust mine with the sheer amount of crap my cousin downloaded onto it.''



``Actually\ldots'' He trailed off, sticking his hands in his pockets.  ``I took my old machine, I replaced the power supply, formatted it, installed a clean OS and done all my usual tricks for clearing out the crap that we'll never use and optimizing it.  You can consider it an early Christmas present.''



She stared at him, and he tried to interpret her expression.  A used computer for a present, would she be offended?  Or, conversely, was she bothered at the idea that he'd given her a two-year-old, two-thousand-dollar machine and that he might want something of equivalent value?



She hugged him for the first time in recent memory.  ``It's great.  Thank you.''



``I know the hardware is two years old, but it's still better than most.''



She hugged him tighter, then let go, ``I don't know how to thank you, and I don't want you to take this as me dodging the subject or being ungrateful, but we really should prep.''



``For sure,'' he smiled.  His body was buzzing from the physical contact.



With Oliver's help, Luke had pulled the couch away from the wall and turned it around, and arranged desks and tables in its place.  Five computers were set in a row.  Noelle and Krouse left their computers off, but the others started up.  A few mouse clicks and the loading image for Ransack appeared.  The game's login screen music played over the speakers of each computer, each out of step with the others.



Krouse looked at Chris and Oliver.  Second stringers.  He'd been one of them, more or less content to watch as everyone else had all the fun.  Oliver was trying to get to a competitive level, but he wasn't very good.  Chris only participated to keep Marissa company and to earn some pocket money.



``Let's talk strategy for tonight's tournament, then,'' Noelle said.  ``Krouse is new, they might not expect him, but Jess is our best overlord.  I think she should go first, Krouse second, I'll follow up, then Luke, then Marissa if we get that far in the best of five.  Any complaints?''



There were shakes of the head.



``We're up against the Chork Pops, North American team.  They'll lead with Mark Key as their overlord.  We know him.  He likes to stall and put every resource towards making a brutal end-boss surrounded by traps and trap spells.  Kind of the opposite of Jess.  I'll take the lead as tank and team captain for round one.  Krouse, you have any idea what you want to do?''



``I've been practicing with an illusion-subtlety-assassin hybrid class.''



``Illusion sucks,'' Cody muttered.  ``And a three-way hybrid?  You're spreading your points too thin.''



\emph{And this is why I'm on the team and you aren't.}



``I take the first opportunity to invade our dungeon, use the subtlety and assassin part of my build to pick them off as opportunities come up.  Our core group's pretty strong, so they'll be fine as a trio.  Since it's normal to fall behind when invading, they won't notice I'm weaker with a shallow point spread.  Endgame stage, I can return to the enemy dungeon to help against the boss, I'll whip out the illusion magic and we'll make a play.  Circle around, or get him to activate the traps too early-''



He stopped as a rumble shook the building.



``What was that?''  Krouse didn't hear who asked the question.  One of the other guys.



The power cut out, the music from the computers cutting off, the lights going dark.



``Shit!  The tournament!''  Luke swore.



The light that leaked in around the edges of the windows dimmed, the curtains simultaneously billowing inward.  Except the windows were closed.



Krouse didn't have two seconds to wonder what was going on before he felt a momentary weightlessness.  He felt himself tipping over, stepped back to catch his balance, and found the floor tilting, out of reach of his foot.



A heartbeat later, the windows were directly overhead, and he was falling.  He started to scream, but he managed only a monosyllabic, ``Ah!'' before he fell onto the side of the dining room table, tumbled to one side and slammed into the chairs, the wind knocked out of him.



Noelle wasn't lucky enough to have the dining room beneath her to break her fall.  Wood splinters flew as she hit the chair.  The table that had held the computers followed her, striking hard and then sliding across the wall to rest against what had been the ceiling.



The wires connecting the computers to the power bar and the power bar to the wall came free.  One computer tower dangled, swung, bounced and fell, a projectile aimed directly for Krouse's head.  He threw himself toward the space under the dining room table, as much as he could with the chairs beneath him.  The computer punched a hole in the wall.



Noelle wasn't so lucky, nor was she as free to move out of the way.  The remainder of the computers and computer monitors came free of the wall and fell on top of her.



The others had been further back, had fallen against the wall that framed the kitchen, to Krouse's right.  He could only hear their shouts and screams, the heavy thuds of bookcases, books, couch and television falling on top of them.



Then stillness, with only the sound of a high, steady scream to break the silence.



The apartment had turned on its side.  The windows loomed high above them, curtains hanging straight down.  Dim light streamed down into the otherwise dark room.



``Noelle,'' Krouse gasped, staggering to his feet.  He climbed over the heap of furniture, tentatively setting foot on the wall to circle around to get to her.



She was limp, blood streaming from her mouth and nose.  She wasn't the one screaming.



``Come on,'' he muttered, making his way to her and carefully dragging her out of the pile of computers.  He checked her pulse: not strong, but there.  Her breathing was thin.



Had to get her help.  Just had to get out of there.  He looked around.  The kitchen door was a solid ten feet above the new `floor', the ledge that the others were on, the wall that had encircled the kitchen, was five or so feet above that.  Every surface around him was flat, featureless, with nothing to climb.



One of the girls on the upper level was muttering, ``Oh god, oh god, oh god,'' over and over.    Marissa or Jess.  The girl who wasn't repeating the words said something he couldn't make out.



\emph{And that keening}, it wasn't stopping.  Didn't she need to catch a breath?  He covered his ears.



It didn't help.  \emph{Must have hit my head.}



``Hey!''  He shouted.  ``We need help!''



Luke peered over the edge, face pale as he looked down at Krouse.



``Noelle's hurt,'' Krouse said, a tremor in his voice.



``Chris is dead,'' Luke replied, oddly calm.



They stared at each other, eyes wide, experiencing mutual shock.  Luke seemed to break free of the spell first, disappearing from sight.



It was a few minutes before Luke returned, throwing down a knotted sheet.



Carefully, Krouse picked Noelle up and arranged her so she draped over one shoulder.  It was awkward; she was nearly too heavy for him to lift.  He managed to keep hold of her with one hand and gripped the knotted sheet with the other, wrapping it around his hand and wrist so he couldn't lose his grip.  He could hear Luke giving orders to the others.  They began hauling him up.



Once he was high enough, he set foot on the doorframe by the kitchen, stepped on the half-inch ledge as they lifted him again, then accepted Luke's hand in getting up to the ledge.



Jess was caught, her wheelchair trapped beneath the couch and a bookshelf, and she had a thread of blood trailing from the corner of one eye, which was bloodshot.



Cody was reeling up the knotted sheet, avoiding looking back at Chris while Oliver attached another sheet at the end.



Krouse glanced at Chris and then looked away.  The boy lay against the wall, his head bisected by the top of the bookcase.  Already, Krouse could detect the cloying odor of mingled blood, urine and shit.  Marissa knelt by her friend's body, holding his hand, unmoving.  She'd stopped chanting in shock.



``What happened?''  Oliver asked, sounding very much like a little boy.  Not that he was.  They were in the same class, the same age.



``Could have been an earthquake'' Luke suggested, still sounding strangely calm.  ``We need to find out how to get out of here.''



``Noelle needs a hospital,'' Krouse said.



``We need a way out of here first.''  Luke looked up at the windows, ten feet above their heads.  Neither the floor nor the ceiling offered anything to grip.  ``All the stuff from the bedroom and closet fell into the front hall.''



``Then we go out the window,'' Krouse said, looking up.  ``We can use the couch and bookcases like ladders.''



The work was grim, quiet, as they moved the furniture, sharing the burdens between four of them at a time.  Nobody looked at Chris, nor did they touch the bookcase that had fallen on him.



Twice, they had to rearrange and reposition the parts of their improvised ladder as resounding impacts shook the building.



Krouse was first up, followed by Luke, who carried Noelle.  As her boyfriend, it smarted to let someone else carry the burden, but Krouse knew Luke was stronger, more athletic.  Going first meant he could help them up and ensure Noelle didn't fall.



He was glad the snow had stopped, but there was a strong wind, and it was painfully cold.  They hadn't brought jackets and gloves up with them, and getting clothes from the front closet would be nearly impossible.  They'd have to find shelter soon.  He perched on the building's concrete exterior, waiting for the others.



He stared out at the city around him.  Snow had been stirred into clouds, and half a dozen buildings had obviously been knocked down, judging by the remaining wreckage.  Luke's apartment building had toppled.  \emph{How did it not collapse in on our heads?}



He turned his attention to his girlfriend, reached over, and squeezed her hand.  Noelle still hadn't woken up.



Cody came up with Jess riding piggyback, her wheelchair abandoned.  Oliver and Marissa were the last to ascend.



``That music,'' Marissa complained.  ``Driving me crazy.''



``Music?''



``Like an opera singer singing a high note and never stopping for breath.  Only it changes a little if I pay attention to it.''



\emph{The scream}.



``You hear it too?''  Krouse asked.  He pressed his hands to his ears to warm them.



``I thought it was a siren,'' Oliver said.



``It's not,'' Krouse replied.  ``It's in our heads.  Try covering your ears.''



One by one, they did.



``What the hell?''  Luke asked.



But Krouse saw Jess' face, the dawning look of horror.



``What is it?''



``I know what it is,'' she said.  She started looking around, twisting around from her perch on Cody's back to search the cityscape around them.



Another earthshaking crash and a flash of light drew their eyes to the same spot.



Three buildings floated in mid air, a distance away, the lower floors ragged where they had been separated from the ground.  One by one, they were hurled through the air like someone might lob a softball.  Even with the impact happening half a mile away, the ground shook enough to make them stumble.



There was a flash of golden light, and the mass of some irregular shape hurtled in their general direction.  The impact seemed mild for the size of the object that landed.  It was hard to make out through the cloud of snow and debris.



Then it unfolded, so to speak.  \emph{No, it isn't that big}.  But `big' was a hard thing to define.



She seemed human, but fifteen or so feet tall, waif-thin, and unclothed.  Her hair whipped around her, nearly as long as she was tall and platinum-white.  The most shocking part of it all was the \emph{wings}; she had so many, asymmetrical and illogical in their arrangement, each with pristine white feathers.  The three largest wings folded around her protectively, far too large in proportion to her body, even with her height.  Other wings of varying size fanned out from the joints of others, from the wing tips, and from her spine.  Some seemed to be positioned to give the illusion of modesty, angled around her chest and pelvis.



Each of her wings slowly unfurled as she stretched them out to their limits, and the snow and dust around her was gently pushed away.  The tips of the largest three wings raked through the building faces on either side of the four lane road, tearing through concrete and brick and bending the steel girders that supported the structures.



She rose off the ground and settled on her tiptoes, as if the massive wings were weightless or even buoyant.  There were parts of her that were see-through, Krouse realized.  Or not quite see through, but porous?  Hollow?  One hand, one leg, some of her hair, her shoulder, they were made up of feathers, the same alabaster white of her skin, intricately woven and sculpted into a shape that resembled body parts, with enough gaps that he could maybe see the empty darkness beneath.



She turned to one side, and Krouse could make out her face.  Her features were delicate with high cheekbones.  Her eyes were gray from corner to corner.  And \emph{cold}.  There was nothing he could point to, no particular feature or quality that could help him explain why or how, but seeing her face made it \emph{harder} to ascribe any kind of human quality to her.  If he'd been thinking she had a sense of modesty before, he didn't now.



She raised one wing to shield herself as a beam of golden light speared through the clouds.  Feathers glowed orange-gold as they were blasted free, disintegrating into tiny sparks and motes of light as the remains drifted away.



The screaming in his head was louder, Krouse realized.   There was a new undercurrent to it, a thread that seemed to point to the sound taking shape, altering subtly in pitch.  What had been a single note was now shifting between two.



``It's the smurf,'' Cody breathed.



``The \emph{Simurgh},'' Jess corrected, her voice small.  ``What is she doing here?  Why is she here?''



``Shut up and run,'' Krouse said.  ``\emph{Run}.''





