





They ran, their feet sliding on the side of the building.  One misstep meant possibly stepping through a window, slicing a leg open, or falling through.  Making things even more hazardous, the concrete of the building's exterior was slick with moisture and ice.  Luke was in the front, carrying Noelle.  Twice, Luke lost his footing, but he managed to keep from sliding through a windowpane.



But it was slowing them down.  There were countless reasons why they couldn't take their time.  The upper half of the apartment building had collapsed, and smoke suggested a fire was spreading somewhere.  There was the fact that Noelle was bleeding, unconscious and might very well be dying as Luke carried her.  And then there was the more \emph{immediate} threat, the Simurgh.  Krouse cast a nervous glance towards the Endbringer, who was rising into the air.



There was another figure there too, higher in the sky.  A man with a muscular physique, golden skin, golden hair and a pristine white bodysuit.  Krouse recognized him: \emph{Scion}.  Definitely not someone he'd ever expected to see in person.



Scion and the Simurgh both moved in the same instant.  A beam of golden light turned the road into glowing dust, and the Simurgh evaded by flying to the left, taking cover on the other side of a nearby skyscraper.  Scion followed, turning the beam her way.  The lance of golden light sheared through the building as if it wasn't there.



As the remains of the skyscraper crumbled to the ground, the already-difficult run across the side of Luke's toppled apartment building became impossible.  Krouse let himself fall, kicking out with one leg to brace a foot against the corner of a window.  He caught Marissa and stopped her from sliding onto the window and falling through.



``Fuck!''  Luke shouted.  ``Fuck, fuck me!''



\emph{Third time isn't a charm for you}, Krouse thought.  Luke had put his leg through a window and his leg was slit open from the base of his foot to his knee.  Krouse belatedly realized his friend was wearing socks.  He'd taken off his shoes as he'd stepped inside his apartment.  \emph{No wonder he has no traction}.



``How-''



He was interrupted as Scion fired another beam further away, following the Simurgh.  It was surprisingly quiet for a weapon that was obliterating three or four hundred feet of road and felling two or three buildings with each two second burst, but the resulting chaos of falling buildings was deafening.  Krouse was torn between staring and averting his eyes in fear; he went with the former: he wanted to be paying attention in case Scion happened to turn the beam their way.  Not that he'd be able to do much.



``How bad is it?'' Krouse finished, glancing at Luke.



``I\ldots I'm not sure.  It doesn't hurt that much.''



``Can you move your foot?''  Marissa asked.



``Yeah.''



``Okay,'' Krouse said, ``Give me Noelle.''



Luke didn't argue.  Krouse crawled on his hands and feet to get to his friend, helping him up.  Then he got help from Luke and Marissa to rise to his feet with Noelle in a piggyback position.  Marissa tied the sleeves of Noelle's sweatshirt together so Krouse could hang the loop around his shoulders.  With his hands, he kept her toes from dragging on the ground.



The fight was getting more distant as Scion continued to fire at the retreating shape of the Simurgh.  Krouse could make out her alabaster form, wings spread, as she swooped and darted between buildings to evade Scion's fire.  The cloud of dust and debris that had followed Scion's attacks in their immediate area blocked his view as they continued their progress across the city.



\emph{We're safe for the moment}.



He turned his attention to their present circumstances.  Luke had no traction, and his leg was hurt, now.  Krouse didn't trust himself to manage with his burden, which meant someone else had to lead the way.  Someone that wouldn't slow them down.



``Marissa.''  \emph{She used to dance.  She's the most sure-footed of us}.  ``Take the lead?  Check our path is clear?''



She nodded.  Her eyes were wide, her gloved hands gripped the zipper-tag of her sweater's collar, fidgeted.  \emph{She's in shock.  Saw her best friend die.}



But she would have to deal.  They didn't have time to mourn, to tend to their wounds or play it safe.  They had to \emph{escape}, before the fight came back this way.



\emph{We still have to get down from here, and we aren't well dressed}.  The temperature, last he'd looked, was supposed to be fourteen degrees Fahrenheit, or somewhere in that neighborhood, but it felt colder.  \emph{If we have to climb}–



Jess shrieked, and Krouse turned his head to see why.  Jess was pressing her hands over her mouth, as if to keep herself from making any more noise.  He followed her line of sight\ldots



The Simurgh.  She was stepping out of the cloud of dust that Scion's attack had left.  As though she were light as a feather, the Simurgh took one step forward and lifted into the air.  She floated down the length of the street one block over, the opposite direction they were traversing the building, her wings folding around her as she landed.



Judging by her lack of a response, the Simurgh hadn't heard Jess, nor had she seen them.



\emph{How is she here}?  He'd seen her disappearing over the horizon, Scion in hot pursuit.  \emph{Did she teleport}?



The Simurgh stopped and raised one hand.  Pieces of machinery began to flow out of a gaping hole in the side of the building nearest where she'd landed, stopping when they reached her immediate vicinity.  A massive box that looked like an oversized washing machine, a large engine with blue L.E.D.s lining it, and tendrils of electrical cords with frayed ends still sparking with live current.



\emph{Telekinesis}.  She'd created a false image of herself out of snow and ice, baiting Scion away.  Judging by the sound of Scion's continued onslaught, she was still controlling it.  Controlling it even though there was no way she could see what it was doing by eyesight alone.



The screaming in his head hadn't let up.  If anything, it was worse: too loud to ignore completely, but every time he paid attention to it, it seemed to distort, rising in volume.  Jess' shriek had brought it into the forefront of his mind, and he couldn't seem to shake it.



``Go,'' Krouse urged Marissa, ``\emph{Fucking} go!''



She moved twice as fast as Luke had, and Krouse tried to follow her footsteps, matching his foot placements to hers to help avoid the spots where there was ice, cracked concrete or snow layered just finely enough to fill the treads of his boots.



Marissa slipped, landing hard, but was climbing to her feet a moment later.  Krouse chanced a look at the Simurgh.  The Endbringer had folded her wings up, forming a protective cocoon around herself, and was relying on telekinesis alone to manipulate the machinery.  She was still calling other things to her, bringing desktop computers through the holes the larger machinery had made, tearing them apart and connecting components.  Insulation stripped itself away from the wiring, exposing metal that moved to entwine and splice into other wires.



\emph{Where are the heroes}?  He wondered, as he turned his attention back to the task of getting down from the side of the building.



No.  The better question to ask was \emph{where is everyone}?  The streets were almost empty, only twenty or thirty people running for cover, hurrying away.  As far as Krouse could tell, the area was deserted.  He felt a chill that wasn't just the cold weather.



They reached the far end of the building, the lowest floors that they could access.  Concrete and rebar jutted out, ragged, where the Simurgh had torn the building free of the ground.



``We're going to have to climb down,'' Krouse said.



``We try that, the concrete's going to crack and we fall.  And we don't have gloves,'' Luke said.  ``If we have to hold on to cold concrete and rebar, we're going to get frostbite.  Or our hands will go numb.''



``Or we'll slip on the snow and ice,'' Jess said.



Krouse leaned forward as much as he was able with Noelle on his back.  It was a solid hundred-foot drop to the street below; there were areas that would be easy enough to descend, where rebar offered handholds and even ladders.  But other spots\ldots there were areas where the concrete might break away under a person's weight, other spots where they'd have to move horizontally, hanging by their hands alone.  Doing it with another person's weight on his back?  With \emph{Noelle}?



``There's no way,'' Marissa said.



``Do we have another choice?''  Cody asked.



``Yeah,'' Krouse said.  Cody gave him a dark look, as if he was being argumentative for the sake of it.  He elaborated, ``If we look inside, maybe there's a place where we can climb through the building.''



``We could get trapped,'' Jess said.  ``If there's fire, or a gas leak, or if the building resettles while we're inside\ldots''



``And if we climb, there's the possibility of fire, wind, or the building shaking.  Let's head through the window,'' Krouse said.



As his less encumbered friends broke the window and climbed through, Krouse stood on the side of the building, his hands tucked into his armpits, watching the Simurgh as she worked.



Cody stood by, carrying Jess.  Like Krouse, he was waiting for others to make sure the way was safe, and hopefully they'd be able to set up a series of footholds or makeshift ladder.



Krouse glanced at the Simurgh.  She was still threading components together.



``She's one of those gadget capes, right?  What do you call them?''



``Tinker.  And she's \emph{not} a tinker,'' Jess said.



Krouse gave her an appraising look. ``Right.  You follow that stuff.  If she's not a tinker then what the hell is she?  I mean, I know the basics, but I never paid that much attention.  Only kind-of, sort-of, following the damage done.''



``She's an Endbringer, obviously.  When she first showed up, she just appeared and hovered there.  Some place in Switzerland.  They thought she was like Scion.  Maybe someone who got a concentrated dose of whatever gives people powers, maybe someone who was in just the right mental state for a trigger event.''



``Trigger event?'' Krouse asked.



``It'd take too long to explain in detail.  The moment when someone gets their powers.  The idea was maybe she and Scion met some specific set of conditions.  So the whole world watched for something like three days, to see if she would be another Scion, or if she'd be something else.   People approached, she even communicated with them some.  Not talking, just gestures, I guess.  Interacting might be a better word.  And when we thought things would be okay, she made a move.  The entire population of the city around her, with all the people who had come to talk with her and research her\ldots''



Jess trailed off, stopped.  Anxiety etched her face.  Marissa was midway through climbing down through the window, looked up at Jess.



``What happened?''  Cody asked.  ``I remember hearing something, but I was a toddler then, and I didn't figure I'd ever actually see her.''



``I don't want to say,'' Jess said.  ``It would distract you guys.''



``Hey,'' Krouse cut in, ``That's not cool.  Not your call to make.''



Jess glared at him.  ``She-''



There was a sudden movement from the Simurgh, tearing sections of wall free from the nearest building, maneuvering them to form a makeshift barrier in mid-air.  Not one second after the barrier was in place, a pair of heroes flew around the corner.  One had a forcefield bubble around him that exploded on contact with the wall, while a woman fired blasts of energy that sent the fragments of concrete plummeting to the ground.



\emph{How did she know}?  The Simurgh had seen them coming?



The Simurgh flexed her wings, and snow raised around her.  Krouse nearly lost his footing as the snow that had piled on the side of the building began drifting towards the Simurgh, an almost gentle push from behind him.



The snow condensed and pummeled the two heroes.  The bubble-man formed another shield around himself, but he left his companion out of it, choosing to interject himself between the Simurgh and the woman.



A section of concrete from a building to the right of the heroes flew free and caved in the costumed woman's skull.  She dropped out of the sky, her head a bloody ruin that Krouse couldn't make out in the midst of the flying snow.



The bubble-man flew forward, aiming not for the Simurgh, but the machinery she'd gathered to one side.  His forcefield swelled, a blue-green that glowed brighter and whiter with every passing second.  Just as he reached the machinery, it reached a critical level and detonated.  The Simurgh was already putting one wing between him and the machinery.  She took more damage than the machine did, and even that was minimal.  Scorched, scattered feathers.



She retaliated, sending rubble, snow and debris in a constant, consistent assault against him.  He raised forcefields to block the attacks, but each was shut down before it could approach critical mass for detonation.  He retreated a hundred feet or so, and the Simurgh began working on the machine once again, giving him only cursory attention.



``Come on,'' Marissa called.



Krouse cast one look at the Simurgh and the lone hero, then hurried to the window.  The others had moved a refrigerator so it was directly below the window, and Luke stood on top, ready to accept Noelle as she was handed down.



It took a second to free her sleeves from around his shoulders, another second to work with Cody to lower her down.



As he watched Cody taking hold of Noelle's arm and waistband, he was struck with the idle recollection that Cody had been one of the people who'd tried to approach Noelle, one of the first to ask her out and be soundly rejected.  He'd nearly forgotten.  It went a ways towards explaining some of Cody's anger.



He had to shake his head and refocus on the task.  Noelle was being handed down to the others at the base of the refrigerator, and the way was clear for him to make his way inside.  He helped Jess down, then they made their way to the front hall.  He opened the closet door and began handing out coats and gloves.  Luke tried on some boots until he found some rubber ones that were big enough.



``How's the leg?''



``Hurting more, but I can still walk.''



Krouse nodded.  With Marissa and Luke's help he got Noelle in position on his back, then opened the door of the apartment and hopped down to the wall beneath.  That left them the task of breaking into another apartment, kicking at the door in an attempt to dislodge it.  Not as easy as it looked in the movies, especially with the threat of falling through and dropping ten or fifteen feet down someone's front hallway.



``It keeps getting worse.  The music,'' Marissa complained.  ``It's like it's stretching between three notes, and the moment I think there's a pattern to it, it changes.''



Krouse glanced at Jess.  What does she know?  To Marissa he said, ``It gets worse if you pay attention to it.  Focus on what you're doing.  Distract yourself if you have to.''



Marissa bit her lip.



The door broke, and they had to catch Oliver before he dropped through.  They climbed down using handholds from the closet door and doorframe, then made their way to the lowest point.



``That smell,'' Marissa wrinkled her nose.



``Raw sewage,'' Luke said.  ``Pipes were destroyed when she tore this part of the building free, probably, and they're spilling out here.''



\emph{It isn't raw sewage}, Krouse thought.  \emph{It's the smell of death}.  People had shit themselves as they died, somewhere nearby.



Wherever they had been when they died, he didn't have to see the bodies.  They headed straight out into the sunlight, stepping onto the snow-covered roads.



The Simurgh was fighting a trio of heroes now, including the man with the forcefield bubble.  Using telekinesis, she was fending off the worst of their attacks and either building or rebuilding parts of the construction she'd been working on.  In the ten or fifteen minutes it had taken to get down through the building and break down the one apartment door, she'd nearly finished creating a complete circle of various components, thirty feet wide.  It looked like only a stray attack had slowed her progress, knocking out a piece of the overarching work.



She made the fighting look easy.  Every time an attack was directed her way, there was something already in place to protect herself or her device.  One cape began to launch ice crystals towards the hoop, and the Simurgh caught the shards out of the air with her telekinesis.  The crystals flew into the man with the forcefield bubble, shattering.  The resulting shards and flakes of crystal didn't fly \emph{away,} however.  They turned around in the air and condensed in a thick shell around the force field.



The ice-encased sphere slammed into the ground with a speed and force that suggested it was the \emph{Simurgh}, not the cape, who was controlling his movement.  He skidded and rolled, the ice shattering first, followed by the collapse of the forcefield.  With momentum still carrying him forward, the cape rolled on the ground, his costume tearing from the friction.



When he finally stopped a few paces from Krouse and the rest of the group, the cape managed to stagger to his feet.  He bled from a dozen open wounds, his skin abraded, his costume in tatters.  He had more ice, blood and dirt on him than he had clean skin or costume.



A tide of snow and ice hit him like a truck, driving him into the ragged edge of the building.  Oliver yelped as he threw himself out of the way.  Marissa's shriek seemed oddly delayed, until Krouse noted what had happened to the man.  The cape, in a bodysuit of velvet blue with gold armor, had been impaled on a tangled mess of rebar, his intestines pushed out the front of his stomach.



It took Krouse a moment to realize the man was actually saying a word, and not just letting out a long, guttural groan, ``Fuuuuuck!  Uuuuunh!''



\emph{``Grandiose down, Z-D-6,''} a mechanical voice blared from the armband that was fixed to the man's wrist.



``I'm not\ldots'' the cape tried to pull himself forward.  ``Not\ldots down!''



``Stop!''  Marissa rushed to the man's side.  ``Don't move!  You'll bleed out if you move!''



The man seemed to notice them for the first time.  His eyes went wide, ``What\ldots doing here?''



``Don't move!'' Marissa said.  She stepped forward, reaching out, and he swung one fist in her direction.  The motion seemed to pull something, because he coughed up a mouthful of blood and folded forward.



``Go,'' the cape grunted.  ``Evac.  Or you\ldots good as dead.  Might be\ldots late already.''



``\emph{Grandiose},'' a voice sounded over the device on the man's wrist.  It didn't quite sound the same as before, ``\emph{She's shut down most of our movers, and}\emph{your time-``}



``No\emph{!''} Grandiose grunted.  ``Have\ldots have time!''



``\emph{I know exactly how fast you fly.  You couldn't get out of her reach in time, even if you left now.}`



``I have time!''



``\emph{I'll let your wife know you fought bravely.  Do you want me to keep a recording for your son, for when he's older?}''



``Dragon!  Damn you!''



``\emph{I'm sorry.}''



The armband beeped, then beeped again a second later.  There was a steady repetition, \emph{beep, beep, beep}.



Grandiose turned his head, ``Why are you\ldots''



\emph{Beep}.



``\ldotsStill here!?  Run!''



Krouse grabbed Marissa and turned to run, barely managing to keep his feet under him with the uneven ground and Noelle's weight.  He glanced over his shoulder to see the cape pressing the armband against his collarbone.



They weren't four paces away when the armband detonated, a small, localized blast that didn't even consume him in entirety.  It did take his head, most of his upper body and his left arm.  The remainder of him was scattered around the surrounding area.



Krouse stared.



``The fuck!?'' Cody screamed, staring.



``Go!'' Krouse said, ``Go, just run!''



They ran, putting distance between themselves, Grandiose's remains and the fighting with the Simurgh.  One wave of capes was retreating, backed up by another squad.  A woman with a black costume, a heavy cape and straight black hair flowing from the back of her helmet led the charge.  \emph{Alexandria}.



The heroine dove at the Simurgh, and the Endbringer was quick to fly to one side, reaching out to catch Alexandria with her telekinesis and use her momentum to force her into the street.  The road caved in, sections of pavement with accompanying drifts of snow falling into a sewer or storm drain beneath the street.



The hoop nearly tipped over, and the Simurgh caught it with her power.  There were four other capes in the area, two on the ground and two in the air, and she was forcing each back with pelted ice and fragments of concrete.



Unmolested, the Simurgh spread her wings wide and rose into the air, towing the hoop of exposed computer chips, wires and assorted pieces of technology after her.  Wires trailed from it to nearby buildings.



``That explosion,'' Luke was saying, panting as he ran with a lopsided gait.  ``They blew up their own person.  \emph{Why}?''



``Because he'd \emph{been here} too long,'' Krouse said.



He glanced over his shoulder, saw the various components of the circle crackling with current as it rose behind the Simurgh, like a gargantuan halo, wide enough that it nearly exceeded her wingspan.



Alexandria was pulling herself out of the rubble, shouted something.  They were a distance away, but her voice could \emph{carry}.



The electricity died, the great circle going dim.  They'd cut the city's power.



``Come on!'' Luke urged them.



There weren't any more people on the streets.  Were they hiding inside, crossing their fingers?  Or had he underestimated how fast people would clear out?



There was a flash behind them.  The hoop was live, with twice the power as before, and the brightness of it made the overcast sky seem dark by contrast.  The snow and dust that the Simurgh and Scion had kicked up weren't helping on that count, either.



The heroes had cut the power, and the Simurgh was still managing to activate the thing.



The heroes had been working in waves, because apparently too much exposure to her, to this \emph{fucking} screaming in their heads that never stopped or let up, it was dangerous somehow.  Only a few heroes fighting at a given time, enough to maybe try to disrupt whatever it was she was up to.  Staying for an allotted amount of time.



Except whoever was calling the shots had seen fit to override that battle plan.  The heroes were arriving en masse now, waves of them, in the air and on the ground.



The Simurgh lifted Lucas' apartment building into the air and tore it into shreds.  The various fragments, the little things, the bodies and pieces of furniture, they became part of a protective maelstrom around the Simurgh, orbiting her and blocking the barrage of long-range fire that the good guys were directing at her.



The screaming was getting worse, \emph{fast.  }It shifted between a half-dozen different sounds, each only vaguely different from the others, a chant, a pattern.



Krouse was wearing a borrowed hat, gloves and jacket, but the jacket was probably better suited for fall weather than winter.  He was cold, his teeth chattering, the temperature sucking the warmth from his body and legs, making him feel just a little more fatigued, a little more tired.



Yet he was drenched in sweat.  It was freezing cold as it ran down the side of his nose to his chin.  His shivers weren't entirely the cold, either.  He was terrified, terrified for himself, terrified for \emph{Noelle}, and for his friends.  Terrified because of the countless little things that didn't make sense, and because he couldn't shake the idea that if he paid too much attention to that screaming, that keening song that the Simurgh was singing in his head, it would start to sound like \emph{words}.



The circle flared with more light than before, and the resulting shockwave threw Krouse and his friends into the air.  Windows shattered and snow was kicked up into clouds as tall as the high rises around them.  The sky visibly darkened with the clouds that had been kicked up, heaping snowbanks dissolved into their constituent snowflakes and water molecules.  The indistinct and distant noises of the heroes firing on the Simurgh had stopped all at once, as the heroes were killed or left reeling from the aftershock of the device's activation.



The protective wreath of flying objects and debris that surrounded the Simurgh slowed, then stopped circling her entirely.  One thing after another dropped out of the sky, as if the Simurgh was consciously letting go of each individual object.



The first of the heroes were already recovering, pelting the Simurgh with long ranged fire or flying up to her to engage in close-quarters combat.  Her wings shielded the worst hits, her telekinesis let her catch or deflect projectiles and she floated out of the way of a handful more.  For the ones who charged in, the Simurgh used thrown debris to strike them out of the air.  One tried to attack the Simurgh's halo, but was struck out of the sky by a flash of electricity before they got within fifteen feet.



A low rumble shook the city, and the gate began to bulge with a dark shape that stretched out from within the metal, like a soap bubble emerging from an enclosed loop.



\emph{Or a lens}, Krouse realized.  It flared bright, rays of light meeting, and things began pouring forth from the point the lines met.   Piles and piles of solid matter flowed down to land at the heart of the city: debris, fragments of architecture, and tiny shapes that were very likely to be people, in a stream as wide across as the Simurgh's wingspan, lit in high contrast by the light of the halo.



And there were tiny shapes that most definitely weren't people, but \emph{were alive.}



\emph{It's a portal.  A door}.



``How the fuck is she not a tinker!?'' Krouse shouted.



``She isn't!'' Jess called back.  ``She's never done anything like this before!''



The heroes were making an offensive push, and the Simurgh moved her halo out of the way of one series of attacks.  The halo tilted at a right angle as she moved it, continuing to spew its contents forth.   Objects and sections of building were scattered across the city.  More than a few things sailed over the heads of Krouse and his friends as they fled.



One figure landed a city block in front of them, contorting itself in mid-air to land on all fours.  It had the vague shape of a man, but dark gray skin like a tree's bark and a froglike mouth filled with jagged teeth.  Each finger and toe was tipped with a claw.



\emph{A monster}.  The thing bristled, muscles visibly tensing beneath its coarse skin as it readied to lunge at them.



Another body landed not too far away, a man with a muscular physique taken to a monstrous extreme, rolling head over heels before he finally stopped.  He might have weighed five hundred pounds, stood eight feet tall, and had an exaggerated bodybuilder's frame, an underbite and a neanderthal brow.  His limbs had been shattered by the landing.  The frog-mouthed thing leaped onto him and began tearing him to shreds.  Easier prey.



Marissa led the group through a side alley, screamed as an object was flung into one of the buildings they were running between.  A stainless steel bathroom fixture, it punched through a window and part of a windowframe, caused a catastrophic series of crashes as it sailed through the interior of someone's apartment.



Something nearby screeched, the kind of noise that reverberated through bones and organs, and Krouse could feel his sense of balance dissolve.  His knees turned to rubber and he nearly ran face first into a wall as his vision swam.



Jess threw up over Cody's shoulder, followed by Cody vomiting as well.  Even as he felt the effects of the sound recede, Krouse couldn't avoid emptying his own stomach.



Noelle stirred, squirmed.  He struggled to change position so she wouldn't vomit onto the back of his head.  The remains of her breakfast, a coffee and a donut spattered on the ground just by his right hand.



\emph{Was that the Simurgh}?  No.  The scream was something else.  Another monster.



``Don't\ldots no\ldots I've tried so hard,'' Noelle mumbled, not even lucid.



``Keep trying, Noelle, stay awake and keep at it,'' Krouse said, struggling to his feet.  The effect had dissipated.  He wanted to be gone before that frog thing gave chase.



Something heavy struck a tall building in front of them, across the street from the alley's mouth.  There was an explosion, and within seconds the building was burning, billowing with plumes of smoke.



Krouse led the way through the mouth of the alley, turned to check on the others and saw Luke on the ground.  He'd fallen.  Marissa gave him a hand standing and supported him as he ran.



\emph{Come on, we don't have time to waste}.



But Krouse wasn't willing to go ahead, either.  They had to stay together, especially with the danger posed by the monsters that had been scattered around the city.  The way he was carrying Noelle, he couldn't check on her, couldn't make sure she was still breathing.  He needed the others with him.



Stepping out into the middle of the street, Krouse had a view of the fighting: the Simurgh was still airborne, and the halo-gate was still active, spewing more creatures and ruined architecture into the streets.



A flash of golden light signaled Scion's return to the scene of the fight.  With one attack, he severed the halo in half, but the portal didn't disappear.  Instead, like watercolor paint, a different perspective began to bleed into the surrounding sky, too bright, too blue a sky, with pale, squat buildings almost glowing in the comparative absence of clouds.  Larger chunks of buildings, massive rocks, and even chunks of earth with several trees rooted in them began to spill out and plunge to the ground.



Scion held back on shooting again, instead charging himself with power.  When he released it, it manifested as a slow radiance, a sphere of light that expanded from him in slow motion.  The tear in reality dissipated, and everything the light touched \emph{stopped}\emph{.  }Shifting clouds went still, objects that were flying through the air ceased moving and simply fell, and the ambient noises of destruction, fire and fighting was replaced by an all-too brief silence.  Even the Simurgh's song, Krouse realized, had momentarily stopped.



The light reached them, swept over them, and he could feel his heart skip a beat.  His entire body hummed with the effect of the stillness, as though he were a tuning fork and for just a moment he'd ceased vibrating.



The Simurgh's movement was slowed in the wake of the light, and Scion took the opportunity to land one well placed shot.  She was driven into the ground like a nail from a nailgun, somewhere Krouse couldn't see.



Luke and Marissa had caught up, along with Cody and Oliver.  Krouse turned from the scene.  He had to hike Noelle up so her sleeves wouldn't pull on his neck, then they ran in the opposite direction from the fighting.



``They're winning,'' Cody said.  ``Beating her.''



``She just dumped who knows how many monsters into this city,'' Jess said, ``And some of them are \emph{here}.  Near us.  We're not \emph{close} to being safe.''



``And Noelle's hurt pretty bad,'' Marissa said.



Krouse grit his teeth.  He didn't want to think about that, about how he was jostling her, how she might be dying as he ran.  He was carrying her, his legs, back and stomach screaming from the hundred-and-fifteen or hundred-and-twenty pound weight he was carrying piggyback, but he couldn't check on her, couldn't see how well or how badly she was doing.



``Luke, are we moving in the right direction?'' he asked.



``I don't know.  Fuck me, this sound in my head-''



``Focus!''  Krouse barked the word.



``It's\ldots I got turned around.  This isn't an area of the city I've spent any time in.  Did she throw us a few blocks?''



``She couldn't have,'' Jess said.  ``The building would have shattered.''



``Then we're on some side street I've never been on,'' Luke said, ``Sorry.''



``\emph{Think}!  Which direction is the nearest hospital?'' Krouse asked.



``I don't know.  I can barely hear my own thoughts over this noise in my head.''



Krouse growled with inarticulate frustration.



``\emph{Ease up}, Krouse,'' Cody said.  ``He doesn't know.''



``Noelle might be dying!''



``-And we'll get to safety first, then someone can take us to a hospital,'' Jess said.  ``But we can't help her if we're hit by some flying piece of concrete or laser beam.  And\ldots they thought that it was better to kill that guy than to let him live, because he'd been here too long.  He'd heard too much of that sound in our heads.  So his own side killed him.  Think about that.  We've been here \emph{longer}.''



Krouse shook his head.  ``But if Noelle-''



``We'll help her, Krouse!''  Jess said.  ``Save your breath for running!''



He grunted affirmation.



They crossed paths with another monster.  A man, pale, with a head twice as large as his torso.  His arms and legs were atrophied, and he crawled, dragging his head along the pavement.  It looked as though he'd sustained some damage in being flung halfway across the city, his head was nearly caved in at the top, a bloody ruin with fragments of skull sticking out.



``Help me,'' the thing pleaded.  He reached out with one emaciated hand.



``How?'' Marissa asked.



``Mars!''  Krouse shouted, ``No stalling!''



She ignored him.  ``How can we help?''



``Give me your memories,'' the monster said.  Marissa backed away a few steps in alarm.  ``Give them!  I want to dream again!  I haven't dreamed in so long!''



Marissa bolted, the hard heels of her boots clacking on the hard ground.



The ground shuddered with a distant explosion.  One of Scion's beams speared into the sky, parting clouds in tidy circles as it passed through them.  There was the sound of something howling behind them.  A minute later, it howled again, closer.  \emph{Is it chasing us?  }



One by one, they each came to a complete stop.  Krouse noted how the screaming in his head seemed quieter.  Were they almost out of her range?



Krouse's eyes widened as he tried to comprehend what he was seeing. \emph{If we are nearly out of danger, then this is some sick joke at our expense}.



``No,'' Luke whispered.  Louder, he repeated himself.  ``No!  Why!?''



A chain link fence barred their way.  It was topped by barbed wire.



In the distance, on the far side of a park, there were squads of men and women in army fatigues, with jeeps and other army vehicles helping to add presence to the already formidable line of defense.  Each of the soldiers was aiming a gun at the fence.



Krouse flinched as a howl sounded, closer than the ones before.  \emph{Caught between a rock and a hard place}.  Not to mention Noelle's condition, or even Luke's.  He winced at the noise in his head.  It was quieter, but his stress here, his alarm and confusion, it was making the screaming spike to a brutally high pitch.



``\emph{Step away from the fence}!''  The voice sounded over a loudspeaker, gruff, authoritarian.  ``\emph{This area is under quarantine!  Seek shelter and wait for further instructions!  If you approach or touch the fence, you will be shot!}''





