





They took a path that kept the fence to their right.  It meant they stayed on the fringe of the Simurgh's power, the volume of the keening song as low as they could hope to keep it, and it meant there was one less cardinal direction that any creatures could approach them from.  There \emph{were} soldiers stationed at the far end of any roads, a ways back from fences, but they weren't taking shots at them.  If the soldiers happened to shout at them through a loudspeaker, he considered it a bonus, something to draw others closer.



He cursed the heavy clouds of fog and dust that were resulting from the ongoing fighting and the snow that had evaporated or scattered on a massive scale.  It wasn't bad enough that there were monsters prowling around the city, but his key senses were being obscured.  He couldn't see more than one or two hundred feet ahead of him, and the noise\ldots there was no absolute quiet.  The screaming in their heads continued without end, low in volume and apparently low in effect, but \emph{there}.  Always there.  Just as distracting and nerve-wracking were the rumbles and the sounds of gunfire, of distant explosions, of buildings collapsing, and of city streets being blasted to shreds.



It was during one of the quiet moments, one of the periodic breaks in the distant chaos where there was only the song in their heads, that they heard a shrill scream.



Krouse, Cody and Marissa stopped in their tracks.



``Was that in my head?'' Krouse asked.



``No.  Definitely a person.  Or people.  We should help them,'' Marissa said.



``We'd be putting ourselves in danger,'' Cody replied.



``No,'' Krouse said.  ``We should go.''



``I feel like you contradict me to be \emph{irritating},'' Cody growled.



``We should go because there's barely anyone around,'' Krouse said, ``And we've got to find a \emph{doctor}.  One person with the right skills in an area with \emph{very few people}.''



``And since someone's screaming, we know there's at least one person there.''



Krouse nodded.  He didn't wait for further argument from Cody, sprinting ahead instead.



His path took him to the foot of a set of tall buildings with stores on the lowest level.  He was somewhat relieved that most of the fast food chains seemed familiar.  Somehow it implied that home wasn't so far away.



Tables and benches were bolted into the ground in a broad patio or plaza between the buildings.  The fixtures that weren't exposed to the winds and shockwaves that were rippling across the city in all the fighting were piled high with layers of snow and ice.



Krouse could hear the crunch in the snow as Marissa and Cody caught up behind him.  He glanced back to verify it was really them, then gripped his spear tighter.



Screams, again.  To his left.



He hurried toward the sound.  He knew the singing in his head was making him more impulsive, rounding off the edges of his sense of caution and pushing him to act rather than plan.  It didn't matter.  He had one goal in mind.



Eight people were gathered in a burger joint with the lights off.  More daunting were the three monsters that were in the room.  One of the monsters was holding a ninth person off the ground.  The windows had been shattered and curls of snow flowed into the fast food place.



Krouse dropped low, crouching behind a snow-covered patio.  He gestured for Cody and Marissa to stop.



The monsters included a man with a neck three times the usual length and a gnarled hump on his back that was plated in armor.   His arms split in two at the elbow, with one set of hands and one set of limbs that ended in built-in scythes.  He was perched on a table, cackling.  His jacket was clearly borrowed, ill-fitting around his hump, and he kept having to push the sleeves up so they wouldn't cover his hands or weapons.



His partner held their victim, the ninth person in the room.  She was big, maybe seven feet tall, and heavy in a way that met some middle ground between being muscular and being fat.  Big boned might have been the most apt way to describe her, in a literal sense.  Her skin was thick, her features blunt: she had a porcine nose and cauliflower ears, her fingers were stubby and her lips so fat that they curled away from her comparatively tiny teeth.  She might have weighed four hundred pounds, and the way she was easily holding her victim in the air suggested she was strong enough to kill someone with one good punch.  She wore only a set of grays that looked like a prisoner uniform.  He could make out the first half of the word that was printed across her shoulders: GWER-.



Rounding out the group was a young woman.  Something was \emph{off} about her, besides the obvious physical changes.  Thick black horizontal lines striped her body, crossing her eyes like a blindfold, extending from the corners of her mouth, lining her chin and tracing down her neck.  By the time they reached her fingers, her skin was more black than white.  She wore the same prison grays, but had donned a jacket and boots.  Her blond hair was straight, her bangs cut severely across her forehead.



She was \emph{off} because there was a rigidity to her.  She stood too straight, and every part of her except her clothing seemed to be drawn in horizontal and vertical lines.



Scythe-arms finished laughing, took a second to compose himself, and then snarled with a viciousness that seemed to be in stark contrast to his previous humor,  ``Ontige hie, \emph{Matryoshka.}''



The massive woman turned to shove her captured victim towards the girl with the lines.  Krouse could make out the rest of the word.  \emph{Gwerrus}.  Her voice was deeper than any Krouse had ever heard. ``Egesa riika se-ji.''



The line girl spoke in a thick accent.  ``Speak the anglo?  This skin too far from myself for me to remember.''



``Mirzuty,'' the large woman swore.  ``Egesa say you take her, Matryoshka.''



``I can not.  Too far.  I will lose myself.  Begging you, Gwerrus.''



Gwerrus slammed her hand down on the counter next to her, demolishing it.  The soft drink dispenser exploded in a spray of fizz and foam.  Gwerrus looked momentarily surprised, and the scythe-armed one started cackling.  Was that the Egesa that Gwerrus had mentioned?



Gwerrus growled, ``There are guards, frail one.  Many.  There are fences and the\ldots what you call them?  Transportation.''



``Trucks,'' Matryoshka said.



``Trucks.  They hunt us.  They have \emph{craft}.  Burn you by looking at you.  \emph{Fly,}'' Gwerrus's deep voice took an almost reverent tone.  ``We must escape.  We use \emph{your} craft to do it.  Fold us.  Fold \emph{them}.''



Matroyshka glanced at the crowd of people that were huddled by the front counter.  Her face was etched with anxiety.  A distant rumble shook the city, and her head snapped to one side in alarm.



``\emph{Ofstede},'' Egesa growled.



``Egesa says \emph{now},'' Gwerrus translated.



``I guess that already,'' Matryoshka said.



``Clever, clever,'' Gwerrus said, with a cruel note to her voice, ``Should use that clever mind to \emph{think}.  Longer we wait, longer we have to listen to this \emph{dwimor} wail.  More time for men hunting us to find us.''



Cody and Marissa crept closer until they were beside Krouse.  Krouse winced as their feet crunched in the snow, but the monstrous people didn't seem to notice.



Matryoshka reached out and bent down in the direction of the woman Gwerrus had thrown to the ground.  Krouse couldn't quite make out the view, but saw a flurry of black and flesh tone ribbons.



When she stood, she had a different face, her hair was darker, and the lines on her face and hands were thinner.



``How long?'' Gwerrus asked.  ``To\ldots what is word?''



``Digest,'' Matryoshka said.  Her accent wasn't so thick as it had been.  ``Hours?  Two or three.  Can't really remember.''



``Fold into me next,'' Gwerrus said.  ``Then Egesa.  Then \emph{them.''}



Both Matryoshka and Gwerrus looked at the huddled captives.



``But if I take more than two or three hours to escape, I'll digest you.''



``I'm a \emph{soldier},'' Gwerrus spoke.  ``Tough.  Hard to eat?''



``Digest,'' Matryoshka said.  ``I don't know.  Not sure you can be \emph{tough} against this.''



``\emph{Efeste,}'' Egesa growled.



``He says--''



``I get it.  Fine.  Kneel.  Easier if I don't have to climb.''



Krouse tightened his grip on the spear, waited until he saw the ribbons.



Then Krouse charged forward.  Couldn't afford to wait until that Matryoshka woman ate someone with the know-how Noelle needed.  The window of opportunity here was small, anyways.  Had to strike while two of the enemies were occupied.



His boots crunched over snow, and Egesa turned his way, raising one scythe before he even saw Krouse.



Krouse drove the makeshift spear into Egesa's side.  The shape of the head didn't allow for much penetration, but it did bury itself in the monster's stomach.



Krouse had never been in a fight.  He'd been punched, but he'd never hit back.  Wasn't in him, he'd thought.  How much of this was \emph{him}, and how much was the song in his head?  Was the Simurgh's song pushing him to violence where he might have tried to find another way in other circumstances?  Or was this what it felt like, doing what had to be done to help Noelle?



Egesa nearly fell from the table he was sitting on, managed to brace himself, and then swung one scythe-arm at Krouse.  Krouse threw himself backward, tugging on his curtain-rod spear.



It twisted as it came free, doing more damage on the way out than it had with the initial thrust.



Egesa fell to the ground, landing with his knees, two scythes and one hand on the ground. His other hand pressed to the injury, where blood was spilling onto the ground.



The hump of a hunchback protected the man's head, as he crouched before Krouse.  Krouse looked at Egesa's arched back, his legs and arms under him.  He could have gone for the stomach again, but there were no guarantees.  He jabbed for the armpit, instead.  \emph{Limit his range of attack}.



His body hummed with adrenaline, and he felt far, far too calm for what he was doing, as he thrust the heavy metal spear into the base of Egesa's arm.  This time he twisted it on purpose before pulling it free.



There was more blood than he thought there'd be, with that one.  Egesa fell over, no longer able to prop himself up.



Changing his grip, Krouse brought the spear down like a bludgeon, cracking Egesa across the head.



When Egesa didn't immediately slump over, Krouse hit him twice more.



``\emph{Ende},'' Egesa growled.



Krouse swung to hit him one more time.  Egesa disappeared in a cloud of black smoke that quickly dissipated and the spear hit tile.



Krouse glanced around to see if Egesa had changed locations.  The scythe-armed freak wasn't around.  He \emph{did} see Cody and Marissa looking at him wide eyed.



This next part wasn't going to change that much.  ``Run!'' he shouted at the bystanders.  They scrambled to their feet and ran for cover.



He advanced on Gwerrus and Matryoshka, saw how Gwerrus was entangled by Matryoshka, wearing the ribbons like a second skin.  Her left arm, completely encased, was compressed to only half the size, almost normal.



Gwerrus looked too tough to hurt, but Matryoshka\ldots  He slashed the end of his makeshift spear into her, and the ribbons of flesh cut and tore.  Matryoshka began to pull together, unwinding from Gwerrus, and he clubbed her over the head.



Gwerrus was a bigger problem.  The way her skin seemed to be three times as thick as normal, at least, and her massive frame, he suspected he wouldn't be able to hurt her with his weapon.  If he-



\emph{No}, Krouse made himself stop, took an account of what he was doing.  He was getting carried away.  He turned to run.



A hand gripped the back of his coat, and a scythe blade extended around Krouse's throat.



He felt another scythe tap against his spear, tapping again shortly after.  He let the spear clatter to the tiled floor.



Matryoshka condensed the ribbons into onion-like layers. The cuts and tears he'd made weren't continuous once she was put together.  Rather, it was divided into a series of short cuts placed around her face and hands, with more probably hidden beneath her clothes.



``Brave,'' Gwerrus growled.  ``Stupid brave.''



``Sculan abretoan cnapa,'' Egesa muttered, just beside Krouse's ear.



Gwerrus shook her head.  ``Na.  Wac thurfan cnapa with huntians ferranan, Matryoshka cunnan fealdan cnapa.''



Egesa shoved Krouse so that he stumbled forward, finding himself in the middle of the three.



``English?  Anglo?''  Matryoska asked.



``We need the boy,'' Gwerrus said.  ``You fold him.''



``Uh huh,'' Matryoshka said.  ``We'll need more.''



``We'll find more.''



``Soon?  Women I just took will be all dissolved.''



``Soon,'' Gwerrus said.



Krouse couldn't help but notice how even her dialect had changed since she'd absorbed the woman into her.  ``You don't have to do this.''



Egesa kicked him from behind, and Krouse fell to his hands and knees.



``Don't hurt him,'' Matryoshka said.



``They are \emph{enemies},'' Gwerrus growled.  ``They hunt us.''



``We're not hunting you,'' Krouse said.



Egesa kicked him again for his trouble, driving a heel into Krouse's kidney.  Krouse grunted and writhed at the pain.  The screaming in his head was bad, now, almost drowning everything out.  It was almost affecting his vision.  He couldn't help but think about the pressure of being deep underwater, being so deep he was barely able to function, except this wasn't imagined.  It was real, despite being all in his head.  That same pressure dimmed everything around the edges of his vision, made shadows darker and lights brighter.  When spots appeared in his vision, he could almost imagine they were images.



Egesa pressed the tip of one scythe to Krouse's eyelid.  ``Abysgian in eage?  Yeh?''



Krouse slipped, so to speak.  He hadn't even realized he was resisting the song, but in the pain, in his momentary fear, he let himself listen, looked at the shapes that were filling the dark places he could see.



\emph{Am I giving up?  This easily?  The others need me.  The others\ldots}



``Noelle,'' he mumbled.



``Francis?''



He winced.  ``Call me Krouse.  Everyone but my mom does.''



``Krouse,'' Noelle tried the word.  ``Okay.  You want something?''



``Just wanted to talk.  When we were marking each other's papers in class, I got yours.  I just wanted to say I like the way you think.''



He could see her expression change, as though the whole paradigm of the conversation had shifted.  \emph{What did I say?}



``Thanks,'' she said.  Her eyes dropped to her lunch tray, and she speared a piece of lettuce on her fork.  She popped it into her mouth and chewed, slowly, methodically, then glanced up at Krouse.  The meaning was clear.  With body language alone, she was asking, \emph{why are you still here?}



``Comparing the way you write an essay to how you'd design a game, plotting things both on a mechanical and general level.  It was interesting to read.  Nerdy in all the best ways.  That's a compliment, in case you're left wondering.''



``Alright.  Thanks.''



He was turning to leave when he saw Marissa Newland approach and sit down next to Noelle.  They weren't people he'd expected to see together.  It wasn't that Noelle was \emph{unattractive}, only that Marissa was a swan, one of the better looking girls in the school, and Noelle was maybe best described as a sparrow.  Small, nervous, plain.  He hadn't imagined they had any shared interest, social circles or friends.



Marissa moved a small plate with a square of pizza on it to Noelle's tray, before looking up at Krouse.  ``Krouse?  You need something?''



``Nah, said what I wanted to say.''



``Don't pester her, `kay?''



``I''m not doing anything more annoying than distracting her from lunch, and I was already leaving.''



``You two know each other?'' Noelle asked.



Krouse answered before Marissa could.  ``Our moms both do a lot of volunteer stuff for the school.  Bake sales and crap.  Been a couple of times where we both got dragged in to help and wound up working together.''



``So I know exactly what to watch out for with you,'' Marissa said.  ``At any given point in time, you're pulling some nefarious prank, you're manipulating others to get what you want, you're making someone else look bad--''



``Stop.  All this praise is going to make me blush.''



``Sixth grade,'' Marissa said, turning to Noelle, ``He tells his teacher--''



``Aaand I'm out of here,'' Krouse said, making sure to interrupt her, ``I forgot Marissa knew about the more embarrassing stories.''



``Good riddance to you, then,'' Marissa said, smiling lightly.



He wasn't two steps away when he heard her saying, ``The Ransack qualifiers--''



He turned, interest piqued.



``What?'' Marissa said.  ``Do I need to get back to the story to scare you off?  Or are you going to make some crack about girls and video games?''



``No, I'm not.  You said qualifiers?  As in competitive level?''



``Yeah.  We have a club we organized through the school, to manage it.  It was the only way I could get access to a computer without my mom looking over my shoulder.''



``No kidding.  That's the same one Luke's in?  You know Luke Brito?''



``Yeah.  He's in the group.''



``Ah,'' he said.  He floundered.  ``I'm sort of lost for words.  The bar for that sort of thing is higher than a lot of people think.  Even getting to the point where you're in the qualifiers is pretty respectable.  Kudos.''



``Thanks,'' Marissa said.



``I won't subject you to my presence any longer.  Good luck tonight.  Really.''



``You play?'' Noelle asked, the question abrupt.  She tore off a bit of pizza crust and popped it into her mouth.



It took Krouse a second to mentally shift gears.  ``Some.  Casually.''



Marissa looked at Noelle to double check, then gestured towards the empty seat across from them.



Krouse sat, winced as a plastic tray clattered to the ground.



Marissa screamed, the sound abruptly cutting off as she was tossed from the counter where the plastic trays were stacked to the ruined counter where the soft drink dispensers had been.  She gasped for breath, struggled to climb to her feet and fell.  She was too dazed, and the ruined counter didn't offer much in the way of solid traction.  Gwerrus advanced on her.



Krouse forced himself back to reality, hurried to climb to his feet, only to feel the scythe's blade press hard to his neck, only his scarf keeping it from severing flesh.



The screaming in his head was back, worse than ever.  After the peace of the memory, the tranquility of being free of the screaming, still experiencing the warm buzz that surged through him, \emph{this} wasn't where he wanted to be.



``Began'na weorc,'' Egesa hissed in his ear.



``Don't understand a fucking thing you're saying,'' Krouse responded.  In a strange way, he was \emph{pissed.  }Pissed in the way he might be if he'd been woken abruptly from a good dream.  He knew it wasn't rational, knew it wasn't even healthy to think that way when the Simurgh was \emph{this} dangerous, \emph{this }insidious, but he was still upset.



So maybe, in the smallest way, it gave him the push he needed to reach beneath his coat, to where he'd stashed the sheathed kitchen knife.  With his other hand, he found and dug his gloved fingers into the wound the spear had made, simultaneously twisting, putting his less vulnerable shoulder in the way of Egesa's scythe-hand.



It didn't matter.  Egesa's knees folded as Krouse twisted his fingers in the wound, dug deep.  The knife's sheath clattered to the ground, and Krouse dragged the blade across Egesa's long neck.



Egesa pushed him away, blood fountaining down the front of his body.  Krouse's fingers were plucked free of the wet, sucking wound as the freak backed away.  Egesa disappeared into wisps of dark smoke.



``Stupid brave boy,'' Gwerrus said.



Krouse glanced around the room as the massive bear of a woman turned to face him.  Marissa was only just managing to stand, while Cody had backed up to the opposite end of the room, crowbar in hand.  Matryoshka was on her hands and knees, not far from Cody.



``Run!'' he shouted.  ``Scatter!''



He was only turning to run away from the brutish Gwerrus when he realized the others might not be in a state to run.  Marissa had been thrown hard, and he wasn't sure what kind of condition Cody was in.



Not that it mattered.  Gwerrus picked Krouse for her target.



She wasn't fast.  There was some small blessing in that.  But he quickly realized that she was keeping up with him, and she didn't have half the trouble he did in wading through the deeper patches of snow.  Slipping on ice, too, didn't prove to be a problem for her when she weighed enough that the ice shattered with each footfall.



She caught up to him before he was clear of the plaza, grabbed him by the seat of his pants and the back of his coat.



He stabbed at her hand with the knife, and felt a fierce agony tear through his own hand.



Blood welled out from his palm, warm as it ran down his arm to his elbow.  Krouse screamed.



``No,'' Gwerrus growled in her deep voice.  ``Stupid boy.''



``Begone,'' a man intoned.



Krouse felt himself slip from her grasp.  He dropped to the ground.



``Do it quickly,'' another man said.



Krouse turned to look, but he saw everything through a monochrome haze.  His own hand seemed smoky, faint.



\emph{I'm a ghost?}



``Any insights, Myrddin?'' a man in armor spoke.  Gwerrus backed away as he advanced.  A giantess and a man in a suit of gleaming armor.  The man twirled a halberd in one hand.



``A protective power.  I just got a glimpse of the idea behind it.  Retribution,'' the first man said.  He was behind the man in armor, wearing a robe.  ``Her power's based around retribution for damage done.''



``Damage reflection?'' the man in armor asked.  ``Or does she get more durable as you attack her?''



``More likely to be the former than the latter.''



Krouse stood as the man in armor walked up to him.  Walked past him as though he weren't even there.



``I am stronger than you,'' Gwerrus snarled.



The armored man didn't reply.



``Why do this?  Why hunt us?''  Gwerrus asked, backing away.



The armored man slammed his halberd down against the ground, and smoke billowed around him.  A moment later, there was a sound like a gunshot.  Gwerrus dropped to one knee, one meaty hand pressed to her chest.



There was a \emph{tink }and she was set on fire, head to toe.



The flames were hot enough and close enough to Krouse that they could have burned him, \emph{should} have burned him.  But he barely felt the warmth of them.  Barely felt anything.  The Simurgh's scream had faded, and his own wounded hand was little more than a dull throb.



``Hey,'' Krouse said, turning to the man in armor.  There was no response.  ``Hey, my friend needs--''



``That was reckless,'' Myrddin said, speaking over Krouse.  ``Attacking when we didn't know the particulars of her power.''



``Two most likely vectors for it,'' the armored man said, talking as though he couldn't hear Krouse.  He raised his voice a little to be heard over Gwerrus' screams.  ``Either she needed to see me, or there needed to be some correlation between me and the damage done.  Smoke plus a nonlethal bullet works as a test for the first case.  Besides, priority one is minimizing interactions, right?''



``Yes.  But it was still reckless.''



Krouse turned to Myrddin.  ``My friend's dying.  Can you help her?''



Myrddin walked ahead, dismissing the smoke with a wave of the craggy wooden stick he carried.



``Dragon?'' the armored man said.



``\emph{I'm here,}'' the woman's voice came from the armbands that they'd fixed around their wrists.



``Myrddin just shunted some kid out to minimize contact.  I saw some blood.  If I mark the location, can we get emergency services here for when he pops back in?''



``\emph{We're overloaded.  Was it}\emph{a severe injury}?''



``Bad, but not severe.''



``\emph{We don't have the vehicles or personnel to spare, and quarantine will still be in effect.}''



``Right.  Where did our target land?''



``\emph{Two hundred feet away, down your four}\emph{o'clock, Armsmaster.}''



``How are we for exposure?''



``\emph{You two are good for another seventeen minutes at the exposure you're facing.  Twenty if we push it.  I can have a flight unit to you shortly.}''



Krouse hurried to follow them as they changed direction and began briskly walking toward the end of the street..



Myrddin spoke up, ``How's the fight going?''



``\emph{It goes well.  But we can't let our guards down.}''



``No,'' Myrddin agreed.  ``This is a bad one.  Too many possible avenues to cover, too much exposure time across the board.''



``\emph{We're doubling down quarantine, and we'll have a processing center in place shortly.  The President is pushing the D.D.I.D measure.}''



``It's going to backfire,'' Myrddin said.  ``I've said it \emph{before}, I'll say it \emph{now}, and I'll remind you all I said it with every chance I get, from now until the day I die.  It's going to backfire.''



``\emph{I don't disagree},'' Dragon said.



``But you're helping to enforce it.''



``\emph{I'm following orders}.''



``No offense, I like you, Dragon, but that's the oldest excuse in the book.''



``\emph{I'm merely picking my battles.}''



``If you're not going to fight \emph{this} battle, then what will push you to make a stand?''



``Myrddin,'' Armsmaster cut in, ``Ease up.  And pay attention.  This is it.''



Krouse stared.  It was a section of building.  White tile and white walls, a desk, and a metal cabinet with a shattered glass pane.  File folders were strewn over the floor and desk.  In the midst of it all was a man in a white lab coat.  His body had been shattered by the impact.



``Damnation.  If we could only look into this\ldots'' Armsmaster said.



``Priority one.  Minimize exposure.''



``I know.  But this stands to answer a great many questions.  If we can find where she opened that portal to--''



``If she's answering questions for us, we don't want to know,'' Myrddin said.



Armsmaster sighed.  ``I know.  Can you shift this into one of your pocket dimensions?''



``I get bad interactions if I transition something in of one of my dimensions and back, or if I take things out of one dimension and put them into another.  It doesn't compartmentalize into the dimension properly if it's been elsewhere too recently.  Whether these people and objects came from somewhere halfway across the globe or some pocket dimension, I don't think we want to test our luck and risk something disastrous.''



Krouse startled at that.  \emph{Is that what happened to me?  }\emph{Some bad interaction of interdimensional crap?}



``I'm thinking white phosphor?''  Armsmaster suggested.  Myrddin nodded.



Dragon chimed in, her voice sounding from the armbands on their wrists, ``\emph{Can't call in a strike until fifteen minutes after the Simurgh is gone.  Mark the area.  I've got another danger site a quarter-mile to your six o'clock.  Then we're getting you clear.}''



``Got it,'' Armsmaster said.



Armsmaster tossed a small canister into the middle of the section of laboratory, they cordoned off the area with red tape, and then they left.  Armsmaster used a grappling hook to fly to a nearby rooftop while Myrddin took to the air.  



With no way to follow, Krouse was left standing there.  He prodded at a piece of rubble, but his hand passed through.



Yet he was able to walk on the hard ground?  He couldn't process it.



``I don't understand,'' he muttered to himself.



``It's not you, it's me.''



He folded his arms.  \emph{That's not something I ever expected to hear}.  ``You can't blame me at least a little?''



``No,'' Noelle said, shaking her head.  She looked miserable, and he felt a knot forming in the pit of his stomach as he saw just how unhappy she was.  It wasn't something he was familiar with, on a lot of levels.  Quiet, she said, ``You've been great.''



He spread his arms, ``I don't get it.  I thought we were doing fine.''



``We aren't!  This is\ldots it's not working.''



``I'm okay with it.  I enjoy spending time with you, and I didn't get any impression you were having that bad of a time, either.''



``But we don't- we aren't--''  She stared down at her feet.  ``We're stalled.  It isn't fair to you.''



``\emph{That's} what you're worried about?''



``Don't dismiss my concerns,'' she said, managing to sound a little angry.



``No', it's \emph{fine}.  It's cool.  I \emph{get} that there's stuff you've got going on that you don't want to tell me about.  I can be a bit of a jerk sometimes, but I'm not an \emph{idiot}.  And I'm not going to twist your arm to get you to share, either.  That's your stuff, and I figure you'll tell me in time.  Or you won't.''



``It's not fair to you,'' she repeated.



``I'm not saying things have to be equitable or balanced or fair or any of that.  So who cares if things aren't fair?''



``Don't do that!''



He spread his arms for the second time in a minute, helpless.  \emph{Don't do what?}\emph{Don't make sense?}



Long seconds passed.  He studied her, saw how dejected she was.  Only minutes ago they'd been having a good time talking.  Then things had fallen apart without warning, and it sounded like she wanted to break up.



\emph{It's like karma for all the times I've pulled shit on others.  Only I did it in fun, and this isn't fun in the slightest}.



``Someone said, a little while ago,'' Noelle spoke without looking at Krouse, ``That I can't really forge a good relationship with \emph{others} until I have a good relationship with \emph{myself.}''



``You don't?''



Noelle didn't say anything.



``\emph{I} think you're fantastic, if that counts for anything.''



``You don't know me.''



``I've been getting to know you some.  And I have yet to see anything that's going to scare me away.''



She stared down at her feet.  ``\ldots{}I don't think we should date.''



``Okay.  If you think that's for the best.  But I just need you to do one thing.  Look me in the eye as you tell me that.''



She glanced up at him, then looked down.  She didn't say a word.



``Because,'' he went on, ``I think you've seemed happier than I've ever seen you since we started going out.  Marissa said so, too.''



Noelle glanced at him.



He continued, ``If you really feel like us dating is making things worse in the long run, then I'm perfectly okay with breaking it off.  I can leave the club if that makes things easier on your end.  It was your thing before it was mine, and you've got enough on your plate with being team captain.''



``I don't want you to leave the club.''



``Okay,'' he said.  He waited for her to speak, but she didn't.  ``Listen, I get the feeling today is a bad day.  Don't know why it is, but it is.  And that happens.  Fine.  But I'm not willing to end this if it's because the stars aligned wrong.  So I'm asking you to tell me that you're worse off because we're together.  Not asking for an explanation, just--''



``Never mind,'' she said.



``Never mind?''



``I'm- just never mind.  Can we forget this conversation happened?''



``Sure,'' he said.  He saw how dejected she looked.  ``Want me to walk you home?''



She nodded.



It was odd.  He'd been punched before, had failed a grade, he'd lost his uncle, and yet it was here, beside his girlfriend, that he was unhappier than he'd ever been.  He was helpless, confused, frustrated.  All he wanted to do was to help her, but he wasn't sure \emph{how.}



He fought the urge to sigh, and drew in a deep breath instead.  The air in his nostrils was so cold he choked on it.  All of his senses were plunged into high gear; a keening song so high pitched it made his ears hurt, cold throughout his body, the smell and taste of dust thick in the air, and pain lancing through his right hand.



Coughing, bewildered, he stared at the pile of rubble and the laboratory.  Whatever effect had encompassed him, it was gone.



\emph{Noelle}.



He scrambled up the pile of rubble.  He remembered how they'd said they wouldn't bomb this site until after the Endbringer was gone, so he still had some time.



He needed a first aid kit.  He went through the cabinets and a set of drawers.  Nothing.  Empty test tubes, glass vials without any contents, canisters without contents, and paperwork.  Lots of paperwork.



His eyes settled on a metal briefcase beneath the desk, within a few feet of the dead man's hand.



His fingers crossed for a portable case of medical supplies, he set it down on the desk and popped it open.  Disappointment overwhelmed him.



Six metal canisters recessed in black foam with slots cut out to hold them, paperwork was set in a flap in the lid.



He swore.



\emph{\ldots{}newly purchased superpowers\ldots}



He winced.  He'd turned his head too fast, and the movement had almost made the song in his head worse, like the pain prompted by moving a broken limb.



As had been the case with the birdcage and the newspaper, Krouse's eye had caught on something.  He'd always been a fast reader, was used to skimming through books, picking up the necessary words.  As his glance had passed over the case, he'd read something in the text without even registering that he'd done it.



He reread the first line, underneath the header.



\emph{Congratulations on your newly purchased superpowers}.



His eyes moved down to the vials.



He slammed the case shut and turned to leave.  There was nothing here he could use for first aid, and certainly no doctors.  He could only hope that Cody or Marissa had caught up with some of the people who they'd rescued from the three monsters.  If there was any justice in the world, there would have been a doctor among them, and Cody or Marissa would have brought them to the house.



He ran.  He had to get back, rendezvous with the others, and get to someone who knew him.  If he didn't hurry, he was worried he would slip into another memory and fail to find his way out again.



The cold air burned in his lungs as he ran, the metal case swinging from his good hand, banging irregularly against his leg.





