





``You made it,'' Cody said.



Krouse stopped in his tracks.  They were more than a block away from the house, and Cody was standing with his back to a wall, in the middle of an intersection.  None of the others were in sight.



He felt a moment's trepidation, saw the way the crowbar hung from Cody's fingers, tapping against the wall.  He couldn't help but read the situation as threatening, but tried to dismiss the thought.  It could have been the Simurgh's influence, coloring his perceptions.



``Yeah,'' Krouse said.  ``I made it.''



``You're hurt.  Sorry if I don't shed any tears.''



``Noelle's okay?''



Cody shrugged.  ``She's not any better.  A little worse.''



``Where's Marissa?''



``I took her back.  She had a bad spell where she froze up.''



``Did you find a doctor?  Even a nurse?''



``Didn't manage to catch up to anyone to ask.  \emph{I'm} okay, by the way.  Just in case you were wondering.''



``I wasn't.  You \emph{look} okay.''



``Sure, but who knows how I'm doing when you look past the surface?  I could be a mental and emotional wreck, putting on a brave face.''



``Cody,'' Krouse had to bite his tongue to keep from saying something he shouldn't.  ``I'm pretty badly hurt, here.  If we have to talk about this stuff, can we at least do it while walking back?''



``Because the Simurgh's been replying old memories for me, and the irritating thing is they aren't my most painful memories.''



Cody wasn't listening.  Krouse walked past him, and Cody turned to follow, talking to him from behind.  ``Not the time my mom had my cat put down, when they definitely could have saved him.  No, every time she brings some memory to the surface, it's \emph{you}.''



Krouse paused mid-step, then forced himself to keep walking.



``Isn't that a pisser?  I get some lunatic alien bird thing speaking in my head, and all she wants to do is make me remember the times \emph{you }irritated me.  The little pranks you pulled, like getting to the clubroom early and fucking with my computer before a game.''



``That was a practice game,'' Krouse said.



``\emph{Before a game.  }I'm there to improve myself, and because I can pull in something a little under minimum wage just by playing and streaming a video of my gameplay online, and because maybe I could get that \emph{fucking} sponsorship, so I could pay part of my way through college.  The sort of stuff that , and you're sabotaging me.''



``It was a practice game, Cody, and it was just a prank that took two minutes to fix,'' Krouse said.  He slowed his pace to let Cody catch up some.  He was starting to think maybe having the guy behind him with a weapon in hand wasn't the best idea.



``Two minutes I was \emph{late to the match}, two minutes where I looked bad to the audience following online, and \emph{we all} looked bad to another serious team.''



``I'm sorry,'' Krouse said.  He wasn't, really.  It had generated \emph{more} viewers, for him and Cody both.  It had been publicity.  He wasn't willing to argue the point; it was more important to get the situation settled down.  ``But can we talk about this later?  You \emph{know} we're on edge-''



``Pisses me off that nobody else sees it.  Pisses me off that \emph{you} don't get that \emph{I} see it.  The smug smiles when you get one over on me, the condescending look you gave me when you first walked into the club, holding Noelle's hand.''



``Cody-''



``\emph{That}`\emph{s} the shit the Simurgh keeps showing me.  Any time I close my eyes, any time I stop for a freaking second, I get it rubbed in my face.''



``She's doing it on purpose,'' Krouse said.  ``Either it's just automatically bringing up the issues that are closest to the surface, or she's doing it because she thinks reminding you of that stuff is going to do more damage in the long run than reminding you of your cat.  You play into her hands if you let it get to you.  You let her \emph{win}.''



``Funny thing is,'' Cody said, ``I'd rather see her win than see you come out the hero, here.''



``She's making you think that way.  That's not \emph{you}, Cody.''



``Maybe.  Doesn't matter.  I'm still going to help out, I'm not going to get revenge or anything,'' Cody said, offering Krouse a humorless smile, ``Because even if I hate your guts, Krouse\ldots  \emph{Francis}\ldots I don't hate \emph{theirs}.''



``Okay,'' Krouse looked at the crowbar, wondered if he'd be able to defend himself with one good hand and the metal briefcase.



``She makes Marissa freak out, she has Oliver crying when he thinks nobody's looking, Jess has gone crazy paranoid, to the point that she's barely talking, if it isn't about looking after Noelle, and apparently Luke can't take his mind off the pain.  But \emph{you're} doing fine, isn't that funny?''



``I'm not fine.''



``Oh?  What's wrong?''  Cody's voice was almost taunting.



\emph{If he doesn't hurt me, I might hurt him}.



``Doesn't matter,'' Krouse said.



``So the mighty Krouse, who gets all the luck, who has everyone wrapped around his finger, who gets the girl and dodges all the consequences, he's not invincible after all.  What's she doing to you?''



``None of your business.''



``Isn't it?  We need to know what's going on.  You could turn homicidal any moment, for all I know.''



``I'm not homicidal.  It's just not stuff I'm willing to talk about with you.''



``Suspicious, suspicious,'' Cody almost sounded like he was having \emph{fun}.



Krouse quickened his pace.  He didn't like the idea that the others were doing that poorly.  He'd had three breaks from the screaming, with whatever power Myrddin had used to shunt him halfway into some other dimension, and the two flashbacks.  Cody seemed functional, if vaguely unhinged, but he'd had the flashbacks as well.



Krouse tried the door, found it locked.  He glanced at Cody, then knocked a few times, loud.



Oliver opened it.  He looked like twenty four hours had passed and he hadn't slept a wink.  Oliver's eyes were red, and he averted his gaze as he saw Krouse and Cody.



\emph{How's she getting to him?  }Oliver's biggest weakness would be his self confidence.  Was she tearing him down like his mother would?  Raising memories of past embarrassments, times people had laughed at him?



Was there a way to fix that?  To support the guy?



Krouse settled for a quiet, ``Thanks, man.  We're going to get through this.  It should be over soon.''



Oliver nodded, but he didn't perk up.



Krouse ventured inside, heading straight for Noelle.



Marissa was sitting at the foot of the couch, head leaning back, asleep or trying to sleep.  Luke had blankets piled on him, having barely moved since Krouse had left.  Jess was in the other chair facing the couch, looking much as Oliver did.



``You're hurt,'' Jess said.



Marissa stirred.  her eyes went wide as she looked at Krouse's hand.  ``We, um- first aid supplies.  We have them.''



``Okay,'' Krouse said.  He knelt by Noelle's head, setting the metal briefcase down.  He could see Cody out of the corner of his eye, leaning against doorway, watching him.



``You ran into people with powers.  Villians?''



``I don't know if they were villains,'' Krouse said, absently, his attention on Noelle.  Someone had cleaned up the blood, but she didn't look good.  Blankets were piled over her to the point that she should have been overheating, but she was shivering.  Eyes closed, she opened her mouth, as if to say something, but her mouth hung half-open, jaw jittering as though her teeth were chattering.



``They were going to kill people,'' Cody said.  ``They were going to kill \emph{you}, last I saw.''



``They were scared people in a strange place,'' Krouse said.  ``They're hearing the same song in their heads that we are, and they barely had any clue how our world works.  I'm not saying they were \emph{right}, doing what they did, but I almost understand it.  Shit, I can't believe you couldn't find a doctor from the people we saved.''



``They didn't know how to find you, after they ran,'' Luke said.  ``They came here to rendezvous.  Marissa wasn't doing well, so Cody went out alone to look for you.''



\emph{Look for me?}  Krouse turned to look at Cody.  \emph{You were waiting around}.



``And I found him,'' Cody said.



``Yeah,'' Luke replied.



``You're a champ,'' Krouse said, offering Cody a level glare.



Cody only smiled a little.  He stepped back out of the doorway as Marissa came through with more bandages.



``I don't know how to take care of this,'' she said.  ``Sprains, yeah, but not this.''



``Clean it and wrap it,'' Krouse said.  ``Listen, I ran into some heroes.  Couldn't talk to them, they wouldn't let me, but I heard them saying something about the fight being almost over. The Simurgh might try to pull something as a final measure, but the heroes were winning, and they were working out what to do after things were done.''



``Really?'' Marissa asked.  She had put a folded towel on the coffee table, and was holding back on pouring the disinfectant on his hand.



Krouse nodded.  ``Maybe fifteen minutes, maybe half an hour.  But it's almost over.  We just need to hold out, stay calm.  Make sure Noelle doesn't take a turn for the worse.''



Marissa poured the disinfectant onto Krouse's injury, and he hissed at the pain, forced his hand down against the table with his good hand, so he wouldn't reflexively pull it away.



``What's this?'' Cody asked.  He advanced from behind, tapped his foot against the metal briefcase.  ``Medical supplies?''



``No,'' Krouse replied.  ``And you wouldn't believe me if I told you.  Give it to Jess.  She'll like it.''



Cody picked it up and carried it to Jess.  She sat the thing on her lap, gave Krouse a wary look, then popped it open.



He waited as Marissa put antiseptic cream on his wound, laid down some thick white bandage pads and started binding it all in place with a cloth wrap.  For all her inexperience with the other stuff, she seemed to know what she was doing with the wrap.



Jess dropped the papers onto the vials without putting them in the separate flap they'd been in, then shut and latched the case.  ``Destroy it.''



``What?''  Cody said.  ``Wait, what is it?''



``Doesn't matter,'' Jess said.  ``Destroy it.''



``What are you talking about, Jess?''  Marissa asked.



Krouse double checked the bandage was in place, then stood.



He approached Jess, and she clutched the case to her chest.  She was almost pleading, ``Put it somewhere nobody will find it, or destroy it.  Mix it with sand and pour it into a hole in the backyard or something.''



``I thought \emph{you} would be more interested in this than anyone,'' Krouse said.



``What \emph{is} it?'' Cody asked.



``Superpowers,'' Krouse said.  ``If I read it right, if I'm not losing it, then the contents of that suitcase tell you how to get superpowers.  I found it with the stuff that got dumped here with the monsters.''



Cody's eyes went wide.  Marissa, Luke and Oliver reacted as well.



``You're not getting it,'' Jess said.



``What's not to get?'' Krouse asked.  ``We're in a dangerous situation.  Is this any different than taking a weapon when we go out there?''



``It's a whole lot different,'' Jess said.  ``It's permanent.  If it works, it's going to change your life.  And that's if it's not a trap.  It could be poison, if it's coming from the same place and the same culture that those monsters did.''



Was it his gut or was it paranoia that told him that she, again, was withholding information?



Krouse cleared his throat, explained, ``I found it in the remains of some office or laboratory.  They were selling this stuff, the papers you were just reading, from the one line I read, suggested this stuff was on store shelves or something.  Why dress it up like that, with a fat pad of paperwork, an expensive suitcase and protective foam padding, only to fill it with poison?''



``I'm not saying it was poison-''



``You did,'' Krouse corrected.



``No, I mean.  I'm just saying.  There's any number of places this could go wrong.  We shouldn't risk it.  Not when we have other stuff to worry about.''



\emph{Yeah, she's being evasive}.



``They're superpowers?'' Cody asked.  He reached for the suitcase and Jess twisted her body to shield him from getting to it.  ``Seriously?  How?''



``Six canisters,'' Krouse responded, but his eyes were on Jess.



``Is that six doses?'' Luke asked.



``Krouse,'' Jess said.  ``Come on.  You \emph{get} this situation we're in.  You know it isn't good.  Don't you want to get back to \emph{normal}?''



``Wait, it sounds like you're saying there's something more going on,'' Luke said.  ``You guys were whispering before.  Is this-''



``Luke,'' Krouse cut him off.  ``Listen, you know me, right?  Better than anyone else here.''



``Pretty much,'' Luke said, but he glanced at Noelle.



``Better than anyone who's \emph{conscious},'' Krouse clarified, though he wasn't sure either way.  ``And you know Jess fairly well too.  So can you trust us when I say that there's stuff going on, and we're acting in \emph{everyone's} best interests if we're not sharing the full details?''



``\emph{I} don't trust you,'' Cody said.



``This isn't some ploy?'' Luke asked, ignoring Cody.  ``You know you've pulled stuff before, and yeah, this isn't the situation for it and normally you'd have more common sense than to try something when things are this screwed up, but if this singing in our heads is making us act funny, then\ldots''  He trailed off.



``It's not a ploy.  If you don't trust me, at least trust the fact that I wouldn't pull something when Noelle's like this.  Even with my head screwed up.  There's bigger priorities.''



Luke frowned.  ``Okay.  I'm trusting you on this.  Don't fuck us over.''



Krouse nodded, expression solemn.  He took a deep breath, then addressed the main issue.  Jess.



``Jess, you're the one that's always followed the superhero scene,'' Krouse said.  ``You follow the lame ass superheroes and villains we've got running around, and the three or four who're maybe actually worth something. You've followed Earth Bet, all the stuff that goes on with the \emph{real} heroes and villains.  And you're saying \emph{no?}  Like I told Luke, that suitcase, it's not my top priority, not even my second or third priority.  Cross my heart.  But this is a pretty big deal.''



``How is this not a priority?'' Cody asked.  ``\emph{Powers}.''



``Shut up!''  Krouse snapped, his voice hard, louder than he'd intended it.



Everyone fell silent.  The only noises were the screaming in their heads, the distant noises of the ongoing fighting, and Noelle making faint noises as she stirred.



Krouse knelt beside her and brushed some hair away from her face.  He turned around and sat so his back was against the couch, holding Noelle's hand.  ``Jess.  Let's read the papers in the case.  Figure out if it's real, a hoax, if we can even use the stuff.  If we can't, maybe we can still sell it.  We could use the money.''



``You don't understand,'' she said.



``I \emph{don't} understand, you're right.  But I can't if you don't explain, and I don't get the feeling you're about to.''



``If you take the papers, you'll decide you should do it.''



``Maybe we should.''



``We \emph{can't}.''



He sighed.



She went on, ``And If I open the case to give you the papers, you'll snatch the stuff, and I can't exactly get up to wrestle  it out of your hands if you do.''



``We won't,'' Krouse said.  ``Just\ldots take the papers out, hand them to us, you can hold on to the suitcase until we've decided.''



``Unanimously?'' Jess asked.



``I don't know about unanimous-'' He saw her expression change.  ``We'll at least discuss it thoroughly.''



She nodded.  She opened the case to grab the papers and held them out.  Krouse reached for them, but it was Cody who snatched them from Jess' hand.



Krouse took a deep breath, exhaled.  \emph{Stay calm}.  \emph{Cody's under the influence of the Simurgh.}



``Six formulas,'' Cody said.  ``Each designed to give different sorts of powers.  It doesn't say what powers, exactly.  Really vague.''



Marissa moved back to Krouse's side, joining him as he checked on Noelle.  His heart skipped a beat at the realization that her teeth had stopped chattering.  He had to put his hand in front of her mouth to make sure she was still breathing.



``This stuff's expensive.  Seven digit expensive,'' Cody said.



Jess shook her head, ``Second page said something about there being a whole battery of physical and psychological tests,'' Jess said.  ``Think about that.  \emph{Why}?  Simple logic here, on why we shouldn't use it.  They think there's a reason someone with psychological issues shouldn't take it, and we're in the \emph{Simurgh's} area of influence.  We're all a little neurotic right now.''



``We can wait,'' Krouse said.



``Not that I'm on Jess' side,'' Luke said, ``But you're contradicting yourself.  You were saying we should use this stuff to protect ourselves, and now you're saying we should wait until everything's over with?  Why do we need to protect ourselves after the Simurgh's gone?''



Krouse shook his head, glanced at Jess.  She wasn't backing him up on this count.



\emph{Because even after the Simurgh is gone, we've still got to get home}.



``I\ldots guess I don't know,'' Krouse said, unable to think of a good response that didn't involve telling the whole truth.



``\emph{Shit},'' Cody said, his eyes going wide.  ``Jess, how far did you read?''



``First few pages.''



``You read this part?''  He folded the front few pages over the back and put the papers in Jess' hands, pointed.



Krouse looked at Noelle, squeezed her hand.  She squeezed his back, weak.



``You awake?'' he murmured.



Marissa leaned over, ``She is?''



Noelle didn't respond.  Krouse shook his head, ``Thought I got a response there.''



Marissa rubbed his shoulder.



``Guys,'' Cody said, excited.



Krouse could have hit Cody.  That attitude, that excitement, when Noelle could be \emph{dying}?  Being so excited about fucking superpowers, when a friend was seriously hurt?



``Wait, look, give me that,'' he took the paper from Jess, ``\emph{Listen}.  `Client three should be informed about the impact of the product on his cerebral palsy, blah blah, legal stuff about liability, no promises, blah, blah, where was it?  Right. Product potentially offers a \emph{mild to total recovery}.''



They stopped.  More than one set of eyes turned towards Jess.



``I-I don't have cerebral palsy,'' she said.



``But cerebral palsy starts with the brain, right?'' Cody asked.  ``That's the most complicated, delicate part of the body.  If something's going to fix your brain, maybe it could fix other stuff.  Let me read more, it's-''



``No,'' Jess said.  ``Even with that.  \emph{Especially} with that, I'm not going to take it.  And I'm not going to let you guys take it either.''



``\emph{Why}?'' Cody asked.  ``Why \emph{especially}?''



``Because!''



``You're getting paranoid,'' Luke said.  ``It's the singing in your head that's making you think that way.''



``It's not!  I \emph{know}.  I've read about this stuff!  About her!  \emph{This} is what she does!''



``What is?'' Krouse asked.



``Why do you think they're so scared?  Why do you think there's a fence with soldiers ready to shoot you?  Do you even get why they're staying out of earshot?''  She pointed at Krouse, ``Why the heroes Krouse saw wouldn't listen to him?''



``Because of the music.  Because we're edgy, unpredictable,'' Oliver said.



``They could use tear gas to manage that.  Or soldiers and guns!  Why couldn't they, with ninety percent or more of the the city evacuated?''



``Then why?'' Krouse asked.



``Because \emph{this} is what she does.  \emph{This} is why she's scary.  Behemoth can turn people to cinders if they're within two hundred feet of him, Leviathan has sunk or leveled \emph{major landmasses.  }Killed\emph{ millions }in one day.  But the \emph{Simurgh }is the one that scares them all the most.  You saw how she fought, the way she dodged and blocked stuff.  She \emph{sees the future}.''



Krouse nodded, ``I kind of guessed that, but-''



``No,'' Jess cut him off.  Her eyes were wide.  ``Listen to me!  She showed up in this city in Switzerland.  First time.  Then after a while, she sings.  Starts throwing buildings around, puts a nuclear power plant in critical condition, spreads winds contaminated with radioactive dust, kills some heroes, drives people to riot and panic with her song.  Like, okay, that's Endbringer standard, right?''



Krouse stayed still, waiting.  He could see Marissa and Oliver nodding.



``Six months later?  A promising scientist commits suicide.  Another person tries to blow up a TV station to get back at his girlfriend.  Superhero assassinates a prime minister and the next guy to be in charge of that country starts a war.  They were \emph{all} there, when the Simurgh showed up.  The superhero's friends said there was no sign, before his encounter with the Simurgh.  He just went downhill, after.  There was other stuff, stuff I don't remember.  But it's all bad.''



``I don't get it,'' Luke said.



``It \emph{keeps happening.  }Every time she shows up.  Every time, people who've heard this song that's in our head?  Things go \emph{wrong}.  They snap, they break, their lives fall apart, or they do something, and it makes something else happen, and there's a major disaster.  That guy who was supposedly making a clean energy source that could power whole cities?  His wife and kids got killed and he became a supervillain who made it a \emph{life goal} to murder anyone who tries to better society with their powers.  There were others.  Over and over, every time she shows up.  She never does quite as much damage as Leviathan or Behemoth, not right away, but stuff always happens \emph{later}.''



``So she\ldots what?  Makes people into murderers?''



``No,'' Jess said.  ``Not exactly.  She doesn't change how you think.  Not directly.  It's more subliminal, like\ldots like cause and effect.  Every time she shows up, she picks a few people, turns them into guided missiles, so they make something horrible happen weeks, months or years after they ran into her.''



Krouse looked at the suitcase.  ``And you think this briefcase is that?  A cause and effect thing?''



Jess offered a short, high laugh, humorless, ``Isn't it?  Isn't it awfully \emph{coincidental} that we got in this situation, \emph{here}, trapped within her range, with Krouse going out to find a doctor for Noelle and finding this instead?  I know what you guys are thinking.  This stuff, maybe it can let me walk again.  If it works.  Maybe we all get superpowers.  But the Simurgh sees what's going to happen.  Probably.  And she's \emph{not} on our side.  However she does it, she's already rigged it all like some Rube Goldberg machine that starts and ends with a mindfuck.''



Luke shook his head.  ``But you can't\ldots if you think that way, then there's \emph{no} action we could take that she wouldn't have predicted and nudged so that it leads to the worst case scenario.''



Jess laughed again, short.  There were tears in the corners of her eyes, ``If she picked us, and that case makes me \emph{think} she did, then we're screwed.  Period.  Every time she shows up, people in her range become walking time bombs.  We don't use the stuff in that case, we still wind up playing the roles she predicted we'd play, and horrible things happen.  But if we \emph{do} use the stuff in that case?  It's the same, we're following the sequence of events she envisioned, only the horrible stuff is worse because everything we do from then on out is a few orders of magnitude more\ldots I don't know.  \emph{Superpowered}.''



``There's got to be something-'' Luke said.  He winced as he shifted position and moved his leg, ``Something we can do.''



Jess shook her head and said.  ``There's no way this works out for us, because she's already seen what's going to happen.  \emph{That's} why I didn't want to tell you.''



Nobody responded.  Krouse looked at the others, saw Marissa's eyes, wide, saw Oliver sitting with his arms hugging his knees.  Luke's face was drawn.



Jess continued, ``Those soldiers outside the fence?  They knew it too.  \emph{That's} why they were scared of us, Oliver.  They think we'll say or do something, and it'll give them some idea, put the right ducks in a row, and they end up dying in a car accident or murdering their wives.  It isn't a quarantine against a disease or a virus or any of that.  It's a quarantine against cause and effect.  A quarantine to limit our ability to affect the outside world.''



``It can't possibly work that way,'' Krouse said.



Jess shrugged.  Bitterly, she said, ``Maybe it doesn't.  Maybe you have to listen to the song, so she can hack your heads and figure out how you'll act, and people are otherwise too complex for her to predict.  The way we act, the fear and all the emotion, maybe it's just a side effect of that hacking.  Or maybe all that's wrong, and she really \emph{is} that powerful.  But \emph{that's} what she is.  She's more fragile than the other two, doesn't last as long in a knock-down, drag-out fight.  But the \emph{aftermath}?''



Jess shifted the case from her lap, shoving it to the ground.  ``The aftermath is where she's worst.''



Krouse stared at the metal case.



It took maybe a minute before Krouse could be sure it was happening, but the screaming began to fade.  Two more minutes passed before it was gone in entirety.



Silence.  Absolute silence, without any screaming in their heads, rumbles of destruction miles away, or ambient urban noise.



That silence was broken when Jess began to sob.  None of the others joined her.  Krouse suspected it was because they had yet to process it.  Only Jess had had the chance to really think through all the ramifications, only she knew enough of the details and evidence to paint a more complete picture and \emph{believe} it all.



Krouse felt damp in his own eyes, more for Jess than himself, odd as it was.  Some of it was exhaustion, the sheer mental strain they'd been under.  He would have stood, walked over to offer support, to reassure her, except how was he supposed to tell someone things would be okay when everything suggested they \emph{wouldn't}?



But he wasn't the type of person who could do that anyways.  He'd never had to, didn't know how.  He was worried he'd fuck it up, and Jess was good people.  She didn't deserve a fucked up attempt at reassurance.



No.  He'd stick to what he knew.  Krouse blinked the tears out of his eyes, cleared his throat, forced a shit-eating grin onto his face.  ``I don't see why everyone's getting so worked up.  How bad could it be?''



Jess made a choking sound, some combination of a sob, a sputter, a hiccup and a laugh.



Krouse saw the incredulous stares, couldn't help but smile.



``\emph{Ass},'' Luke said, but he smiled too.



Cody turned, stomped off, kicked something hard as he passed through the front hall.  Any miniscule lift in the mood faded in his wake.



The room descended into silence again.  \emph{At least}, Krouse noted, \emph{Jess isn't crying anymore.}



Krouse was still holding Noelle's hand, his fingers interlaced with hers.  He pulled her hand towards him and kissed the back of it.  His eyes settled on the metal case.



\emph{Maybe it wasn't us,} he thought.  \emph{Maybe she picked a bunch of other people, and dragging us into this world was just something that happened}.  \emph{Maybe we'll get Noelle fixed up, we'll find our way home, and all of this winds up being some scary memory}.



He huffed out a breath, a silent, derisive, one-note laugh.  He'd managed to distract or trick Jess into feeling just a tiny bit better.  \emph{But even telling myself something that ludicrous,}\emph{I can't do it for myself.}





