





``We have to tell them,'' Krouse murmured.



He and Jess were in the kitchen of a stranger's house, using that stranger's utensils to prepare their food.  It felt odd, invasive.  \emph{Except it's not like they'll be coming back any time soon}.



``I need another knife,'' Jess said, ``This one's awful.''



``Are you dodging the subject?''



``No.  I need a better knife if I'm going to keep cutting strawberries.  We can still talk.''



Krouse opened a drawer and passed a knife to where Jess sat on a stool at the counter.  ``They're going to find out sooner or later.  I've noticed something like five major clues since I started paying attention.  They're distracted for now, but--''



``This knife sucks too.''



``All the knives suck.  Whoever lived here didn't take care of their stuff.  Make do.''



Jess set to cutting the tops off the strawberries.



``They're going to be upset,'' she said.



``No shit.  We're stuck in a whole other world, and things are \emph{just} different enough that we could fuck up and reveal ourselves as aliens.''



Jess nodded.  She gathered a mess of strawberry tops from the cutting board and strained to reach forward enough to get it in the empty plastic container.



Krouse put one foot on the bar of the stool to give it a little more weight, so it wouldn't fall, then moved the plastic container closer.



Jess said, ``That would be bad, if we got caught.  The people of this world?  They're scared.  There's \emph{laws} against people or objects being transmitted across worlds.  When that hole between universes came about, the first idea on people's minds was that we might go to war, a whole other planet with resources.  Water, oil, wood, metal, all that stuff.  And Earth Aleph would lose because Bet had all the capes.  The rest of the world thought this gateway would make America into a bigger superpower than we already are.  So there were sanctions, deals.''



Krouse nodded.  He flipped the pancakes over on the frying pan.  They were the crappy sort, the sort that came from a box.  Still, it was better than nothing.



``It's bad, Krouse.  Even if we were willing to go home, with the Simurgh maybe planning something--''



``We can't let that dictate our choices,'' Krouse said.  ``We'll go crazy trying to second guess everything.  We \emph{can} minimize the damage, try to keep a low profile.  And I'll admit you're right.  Not using the contents of that briefcase is a start.  If we get a chance to meet the president or something, we should probably turn it down.''



``Yeah,'' Jess said.  Then she held up a hand.  ``Shush.''



Floorboards upstairs were creaking.



Marissa came downstairs, her hair wrapped in a towel.  ``Shower done, if either of you want to rinse off.  We have power?''



``Came on a bit ago,'' Krouse said.



``Got restless, decided to do something.  Food in our bellies, keep the furnace burning.'' Jess said.  ``Hungry?  Offering up some pancakes for dinner.''



``Yeah,'' Marissa said.



Krouse checked the pancakes and put them on a plate, tearing one in half and popping it in his mouth.  ``Mars, you want to relieve Oliver?  He's looking after Noelle right now.''



``Who took the shift before that?''



``Me,'' Krouse said.  ``I'll bring you a plate.  Butter and Syrup?''



``Sugar and lemon juice,'' Marissa said, before leaving for the living room.



Krouse spoke in a low voice, ``We \emph{have} to tell them.''



Jess nodded.



Krouse opened his mouth to say something else, then shut it as conversation erupted in the living room.



\emph{Noelle}?



He turned off the oven burner and headed in that direction, only to be stopped by Jess.  ``Krouse?''



He paused, looked back, saw her perched on the stool.



``Bring me?''



He grimaced, sliding one arm around her shoulders, with his other one beneath her knees, making sure not to bump his injured hand against anything.  He lifted her and commented, ``You're lighter than I thought you'd be.''



``Ever a charmer, Krouse.''



``Guys!''  Marissa called out.



Krouse hurried for the living room, pausing only to ensure he didn't slam Jess' head or feet into a door frame.



His blood ran cold as he saw what had the others attention.  It wasn't Noelle.



The television was on, and it was displaying footage of the Simurgh.



``\emph{Shit},'' Jess whispered.



``We have cable!'' Marissa said, smiling.



``Maybe we'll have working phones soon,'' Luke said.  ``Get ahold of our parents.''



Krouse navigated past where Oliver was lying on the ground, blankets balled up so he had something to lean against, a book in his hands.  He stepped around the coffee table and set Jess in the one empty armchair.



Then he walked over to the TV, blocking it with his body, and pressed the volume button at the top until the sound was off.



``What the hell, Krouse?'' Luke asked.



``Asshole,'' Cody said.  He was sitting in the adjacent dining room.  ``We might finally get a chance to find out what's going on.''



``You're going to find out because I'm going to tell you,'' Krouse said.



``What the hell are you talking about?'' Luke asked.  ``Is this that thing you were putting off telling us yesterday?''



Krouse nodded.  He saw Jess shifting position as though she were trying to face everyone else, met her eyes and shook his head just a little.



She frowned, but she kept quiet.



``Spit it out,'' Cody snapped.



``We're a long way from home,'' Krouse said, shrugging.  ``Better you hear it from me than find it out on TV.''



Marissa frowned, her eyebrows knitting together.  ``Long way from home?  But--''



``We're still in Madison.  We're just\ldots we're not in \emph{our} Madison.''



He stopped to let that sink in.



``Oh \emph{fuck you},'' Cody snarled.



Oliver was looking around the room, seeing people's expressions change.  He looked at Krouse, ``I don't understand.''



``When the building fell, that was her bringing us through?'' Luke asked.



``Yeah.  From Earth Aleph to Earth Bet,'' Krouse confirmed.  He saw Oliver's eyes widen as he belatedly understood.



``Wait,'' Marissa said, ``But\ldots \emph{what}?''



``You knew too, Jess?'' Luke asked.



``I- yeah.  Yeah, I figured it out.''



``It's what we were talking about, after we first got to this house,'' Krouse said.  ``I convinced her to keep quiet.  Figured it wasn't crucial to know just then, and with the screaming in our heads, we didn't need the added stress.''



Jess stared at him.  He glanced at her, then turned his attention to the others.  \emph{I'm better at being the bad guy than you are.}



``You had \emph{no}\emph{right},'' Cody said.



``Probably not.''



``So you were keeping us in the dark?'' Luke asked.  ``Deciding it was for our own good, deciding \emph{for us}?''



``That's the gist of it.  I think you'll look back on this and see why I did it.  We needed to look after ourselves, look after \emph{Noelle, }and we couldn't do that if we were thinking about how we had no way of getting home.  I strong-armed Jess into being quiet, hid one or two pieces of evidence.  Hate me if you have to, but it made sense.''



``But we- is that why you told us we should stay here instead of heading out?''



Krouse shrugged. ``Part of it.  Another part of it was just like I said; we can't be sure the heroes have found and defeated all the monsters the Simurgh dropped into the city.  Maybe they won't ever get all of them.  But yeah, no point leaving because there's no home to go \emph{to}.''



``But how--'' Oliver started.



He didn't get a chance to finish.  Cody was on his feet in an instant, his chair falling to the ground.  He rushed Krouse, gripping him by the shirt collar.  Once he had a hold, he swung Krouse around to one side, shoved him, throwing him across Jess' lap and into the coffee table that sat between her and Luke.



Luke tried to stand from his chair, but Cody pushed him back down.  While Luke fell back, Cody stooped down to seize Krouse's shirt with one hand, striking at his face with the heel of the other.



``You \emph{fucker!  }Lying to us?  At a time like this!?  Fuck you!  \emph{Fuck you}!''



Krouse tried to shield himself with his arms, but it didn't help much.  He brought his knees up to his chest, between himself and Cody, then kicked outward, forcing Cody off.



Cody fell back, nearly hitting the coffee table in front of the couch.  It would have been a good opportunity to close the distance, to hit back, but he didn't.  Krouse took the opportunity to stand, tenderly touching the spots on his cheekbone, chin and nose where Cody had landed some good hits.



``Fucker!''  Cody shouted, from across the room.



``I\ldots well, I guess I deserved that,'' Krouse said.



``Krouse--'' Jess started.



``Hm?'' he turned her way, touched fingertips to his nose to check for blood.  \emph{Only a little}.  ``It's fine.''



\emph{Better they're mad at one of us than both of us.}



``Fine?'' Cody growled.  ``We're fucking stuck in a world with Endbringers like that psycho alien bird bitch!  And we've got \emph{you} playing head games with us on top of that!''



``He wasn't playing head games,'' Luke said.  He winced as he moved his injured leg from his footrest to the ground.  Not exactly.''



``Thank you for saying so,'' Krouse said.



``Don't thank me,'' Luke said, angry, ``I'm not on your side.  I'm just saying you didn't fuck with us for your own gain, you fucked with us because you thought it was in our best interests.''



``So that's it?'' Cody asked.  ``It's not just that we're pawns in some crazy chess game the Simurgh is playing.  We're stranded here?''



``Yeah,'' Jess said.  One word.



``There's got to be ways home,'' Luke said.



``Probably,'' Krouse replied.  ``But they won't be easy to find.''



``What are we supposed to \emph{do}?'' Oliver asked.  ``If we go to the police--''



``They'll realize that we're probably pawns in the Simurgh's game plan,'' Krouse said.  ``We'll be detained.  And let's not forget, they killed that superhero, because he \emph{might} have been caught in her web.  Odds are pretty fucking good that \emph{we're} caught in it, between the coincidences Jess mentioned and the fact that the Simurgh pulled us from our world to this one.  The people in charge?  They won't fail to notice.''



``You think they'd kill us?'' Oliver asked.



``It's hard to believe, but I find it hard to believe they killed the cape and they did.  Yes.  I think they'd kill us..''



When a minute passed and nobody spoke up, Krouse turned the volume up for the television.



``\emph{\ldots{}final decisions.  In the meantime, plans are underway to build permanent blockades around the affected area, with concrete walls placed South Midvale Boulevard to the west, Capitol Square to the east, and Haywood Drive to the south.  A quarantine processing center is already established at St. Mary's Hospital, servicing city residents who were not evacuated before temporary blockades were set up.}



``\emph{Restitution will be offered to citizens displaced from their homes, paid for with international funding.  Authorities report that no catastrophic damage was done, and the situation was quickly brought under control by the first responders to the scene.  Chicago Protectorate leader Myrddin is quoted as stating, `This is a win for the good guys.  Scion arrived early to put the pressure on within minutes of her arrival and Eidolon delivered the final blows, driving her off.  We're getting better at fighting these guys, and it's showing.'}



\emph{``However, insider sources in the PRT suggest that things are not so glowing.  A vault holding the equipment of now-deceased supervillain `Professor Haywire' was accessed by the Simurgh.  Shortly after, the source alleges, the Simurgh activated a large-scale replica of the devices, depositing large amounts of foreign bodies in the heart of the city.  Among these bodies, multiple reports say, were innumerable monsters with superpowers and hazardous materials.  When asked, the Chicago PRT director declined to comment, except to say that there have been no breaches of quarantine and there is no indication of risk to anyone in the vicinity of the quarantine zone.''}



``MWBB \emph{coverage of the Endbringer attack will continue for the rest of the day, but next, we have a story of-}''



Krouse turned off the TV.  ``St. Mary's?''



``Not in our world,'' Jess said.  ``And we're running a lot of risks by going\ldots''



``We don't have a choice,'' Krouse said, looking at Noelle. ``We'll find a map, and we'll need a car, with half of us unable to walk.  Let's get Noelle to a hospital, ASAP.''



\sectionbreak



Finding the car proved to be the hardest part.  There wasn't a car in the garage of the house they were borrowing, and though Krouse saw a car in the driveway of the neighboring house, he couldn't find a set of keys in any of the obvious locations.



\emph{Be nice to know how to hotwire a car}.



In the end, they headed out as two teams.  Krouse was joined by Marissa, while Oliver and Cody formed the other team.  It was dark, the streets were empty, and snow still drifted in dense clouds.  Few places had lights on, but that proved fortunate, as those places tended to be businesses.



They found a car rental place, but metal shutters on the window barred their access.  \emph{The keys are probably in a safe or something}, Krouse thought.



They ran at first, jogging lightly as they hurried from place to place.  As they ran into continual failures, failed to find a car they could use, they slowed to a brisk walk.  It meant preserving their stamina, even as the slowness of it made Krouse anxious.  Every second spent looking was a second that Noelle had to wait.  Settling in and leaving her to linger in a nigh-unconscious state had been their only option before they'd heard the broadcast.  Now, though\ldots



They passed the area with the restaurants and patios as they continued searching for a usable car.  Every time he passed a car, he peered inside to see if there was a key in the ignition, if maybe it had been left abandoned by the owner.  No luck.



\emph{This is pointless.}



He checked another car, wiping snow from the window, then hurried to catch up to Marissa.  She was checking the cars on the other side of the street.



``No luck,'' she said.



``Can I ask what you saw?'' he asked.



``What?''



``When the Simurgh showed you stuff.  What did you see?''



``Why does it matter?''



``Because I'm trying to get a sense of what her game plan was.  Cody told me that she reminded him of \emph{me}.  Brought up all the bad memories of times I gave Cody a hard time, times he thought I slighted him or whatever.  I'm wondering if it was the same for you.''



Marissa shook her head.  ``If I say no, will that be enough?''



``I won't force you, obviously.  But\ldots I've been trying to think about all this the way \emph{she}`\emph{s} thinking about it.  Anticipate her moves.  It'd help a lot if you shared.''



Marissa made a face.  He couldn't \emph{see} a lot of her face, with the white scarf that was wrapped around the lower half, but he saw the grimace, the skin wrinkling on her nose.



``Okay.  It's fine, don't stress about it,'' he said, hurrying to check more cars on the other side of the street.



She called out after him, ``I was on stage!''



He stopped, turned.



``I was on stage.  It was just before I stopped doing all the dance and music stuff.  The whole thing then had been lyrical dance.  But I'd been rebelling\ldots''



She trailed off.



``I don't follow.''



``I was fighting with my mom, top of our lungs screaming at each other, always about stupid stuff.  The color of my dance uniform, and what I was eating for dinner, the amount of homework I was or wasn't doing.  So I stopped practicing.  Started hanging out with friends like I'd wanted to do for years.  Thought I was getting back at my mom, that I'd get on stage, and I'd get fourth place, and she'd be \emph{pissed}, whatever.''



``But?''



``I froze.  It's never really happened to me before.  My mind went blank, I, um, I couldn't even bring myself to move, or pull one coherent thought into my head.  I was sweating, breathing hard, to the point that I almost thought I'd finished, except I hadn't even started.''



``Scary.''



``It's\ldots it's worse than that, but it wasn't scary so much as\ldots devastating?  I don't know if I explained it right, but it's like, I managed to get a little of my \emph{own} strength, break away from my mom's grasp, and all the pressures she put on me, become my own person.  And then I'm standing there on stage, and I feel a bead of sweat run down the inside of my leg and for just three seconds, I-``



She stopped.



Krouse didn't want to interrupt, and Marissa was busy talking, so he took over checking the inside of the car windows as they walked.  He peered inside the next car. ``You thought you'd pissed yourself.''



``\ldots{}I don't know why I said that out loud.  You fucking mention that ever again, and-``



``I won't.''



It was another ten seconds before she continued.  ``I must have turned bright red.  I'd felt strong, felt independent for the first time in my life.  And then it turns out like \emph{that}.  And she's in the audience, front row.  My mom.  She's \emph{smiling, }because she thinks it's a victory for her.  The rebellious daughter discovering that mom was right about everything after all, you know?  That's how she probably saw it.''



Krouse nodded.



``That smile?  That was what the Simurgh showed me.  Except it lingered.  Couldn't shake it.  Almost as if it was the Simurgh doing it and not my mom.''



Krouse scraped at ice that had packed against one passenger-side window, peering inside.  ``What happened after that?''



``Here or back then?''



``Back then.''



``I had a bit of a breakdown.  My grades went to hell, I stopped doing \emph{everything}, all of the music, all of the dance, all of the after school stuff.  Retreated to my room.  Wound up going to therapy, but my mom sat in on all of the sessions, and how could I get better when the person that's ninety-percent to blame for the problems is in the room with me?  Stopped going to \emph{that} therapy until I could get a therapist who'd be for me and \emph{just} for me.  That's where I met Noelle.  Chris backed me up in general, but it was Noelle that helped me find my way.''



He could see her face fall, understood why.  ``I'm sorry about Chris, by the way.''



``He was a genuinely good guy.''



``Yeah.  Sorry I didn't get to know him more.  He was always more your friend than \emph{our} collective friend.  But he was nice enough.''



``And without Chris or Noelle, there's nobody left in the group that I really could talk to,'' Marissa said, ``So it's the same for me, now, kind of.''



``Yeah,'' he said.  ``You can talk to me, if you need to, you know.''



She snorted.



There was a break where they only investigated the cars.  Krouse knew he should be on the other side of the street, looking for keys, but it was fruitless.  There was an expensive looking hotel at the end of the street that had a parking garage, and he held out hope that the place would have valet parking.



Oliver had been saturated with self-doubt, loathing, all the things that made him introverted, passive, even whiny.  He'd been brought to tears at one point, even.  Marissa had been brought back to the stage, her focus turned to her relationship with her mom.



\emph{What purpose does that serve?}



The only thing that Krouse could think of, and he had to ask Luke to get a third data point, was that the Simurgh had wanted to distract them.  Cody, meanwhile, had been set against Krouse, and Krouse's attention had been turned to Noelle.



\emph{This doesn't strike me as the kind of maneuvers she'd be making if she was planning something for years from now}.  \emph{This is more imminent.}



``What are you thinking?''



``That I need to talk to Luke about what he saw.''



``To make sure he's okay?''



``That, and to round out my theory.  With your situation, what you were talking about with the aftermath of the stage fright, was that it?  There was nothing afterward?  Things got better?'' he asked.



``Yeah.'' Marissa shrugged.  ``It was good to be free, to have time to myself, without my mom, um\ldots''



``Your mom's intensity?''



``Intensity.  Yeah.  But it sucks, because I'm a year away from the point where I could move out.  Maybe more, depending on how long it takes me to get first and last month's rent together.  And until then, I've got to put up with dinner conversations where every other sentence has a hidden barb, a prod to \emph{accomplish} something, or a dismissal of the stuff I'm actually interested in.''



\emph{She's talking like all that's still a consideration}.  \emph{We're a long way away from that stuff, from our families and having to worry about rent}.  Krouse knew she'd feel worse when it hit her, if she kept thinking that way.



``You don't need to worry about any of that now, at least,'' Krouse said, trying to sound nonchalant, checking the next car.



He didn't hear a response.  Turning back, he saw her eyebrows drawn together in a frown.  He asked, ``Sorry.  Was that too blunt?''



``No.  Um.  I dunno.  Is it strange I miss my mom?''



``You know your feelings better than I do.''



``For years, I've dreamed about running away, or getting enough money together to move across the country and cut all ties with her.  Only now a situation like that's been dropped in my lap, and I realize I might not see her for a long time, if ever, and Chris on top of that\ldots''



``I think these circumstances would make anyone feel lonely,'' he said.



Marissa nodded.  ``How are \emph{you} holding up?''



``Just want to get Noelle help.''



``And your hand?''



``Hurts like a bitch.  But it feels silly to complain when we have bigger problems and other people are hurting more.  And I'm getting antsy, taking so long doing this.  Looking in the car windows isn't getting us anywhere, and it's getting too dark.  Let's check the hotel.''



``Okay.''



They crossed the street and found the front door of the hotel unlocked.  Only half the lights were on, set for daylight rather than evening, and the interior was abandoned.



``Everyone really did evacuate, didn't they?''  Marissa asked.



Krouse hopped onto the front desk and swung his legs around to the other side before hopping down. ``Two ways to deal with the Simurgh, I guess.  Far easier to be preventative than to clean up the mess afterward.''



He opened a drawer and found a mess of business cards, each organized into neat rows with elastic bands around them.  The next drawer was locked.  ``Mars!''



Marissa returned from the employee-only hallway beside the front desk, ``What?''



``Can't get this open with one hand.  Want to try?''



She tried and failed to get the drawer open.  Struck by inspiration, she hurried back into the hallway and then came back with a toolbelt.  It took less than three minutes to get the drawer open.



Half of the drawer were largely empty, containing only two credit cards, a piece of jewelry and a paper noting procedure for managing the lost and found.  The other half of the drawer was sectioned off with a grid of wood panels, with keys and slips of paper in some and plastic cards with numbers in stylized golden letters in the others.



``Score,'' he said.



A dozen keys in hand, they made their way to the parking garage, stopping at the stand with all the brochures to find one with a map of the area.  Marissa got in the first car they found.  Testing the remaining keys, Krouse made another nearby car beep.  \emph{Seven of us, and Noelle should lie down.  This works}.



They opened the metal paneled door to the parking garage and hurried back to their cars.  He followed her out.



The plan had been to loop around and find the others.  If they couldn't, they were to beep and signal them.  With things this quiet, it wouldn't be too difficult to hear the horn.  Still, he'd rather not have to.  There was no guarantee the freaks weren't still around.  Two people would be hard to spot in the gloom and the curtains of falling snow, but cars with glowing headlights?



Oliver and Cody were nowhere to be seen.



He beeped twice and waited, while Marissa drove ahead and did the same.  A minute passed as they staggered their movement across the area Oliver and Cody had headed off to.  The pair didn't show up.  Either Oliver and Cody were in trouble, or-



He peeled out, driving past Marissa.



Was the gut feeling his own, or was it something implanted in his head by the Simurgh?



The wheels skidded on the snowy surface of the road.  He didn't have far to go.  If he was wrong, he knew this would cost them only a little time.  If he was right, though-



There would be a car parked outside the house.  There was; Cody had left it sitting in the middle of the street, by the fence.  Krouse pulled his car to a stop and climbed out.



The soldiers on the other side of the fence were still there.  All but a few were inside their vehicles, now.  Others were outside, smoking.  They didn't seem to care about what was unfolding ahead of them.



Krouse rushed into the house.  He glimpsed at Noelle.  She didn't seem to be any worse, and Oliver was beside her.  Jess shot him a concerned look, but Krouse wasn't waiting long enough to exchange words.  He rushed towards the kitchen.



Luke was standing, one leg bent and off the ground, holding a door frame for balance.



``Cody--'' Luke started.



``I know,'' Krouse replied.



There was a noise as someone ascended the stairs.  Cody burst into the kitchen.  ``Where are they!?''



``And you call \emph{me} the asshole,'' Krouse said.



``Fuck you.  You hid them.''



``Close, but no cigar.  We \emph{did} leave the suitcase in plain sight, took the canisters out.''



``Where!?''



``But we didn't hide them.  Jess and I destroyed 'em, before we started cooking dinner.''



``\emph{Bullshit}.''



``We weren't going to use them,'' Krouse shrugged.  ``It's a bad idea.''



``You fucker!  Making decisions for the rest of us!''



Krouse shrugged.  ``\emph{Cope}.''



Cody turned towards the area where Luke was at the door frame.  ``Luke.  You're going to stand by and let him act-``



``You don't have any ground to stand on,'' Luke said, interrupting.  ``Not that Krouse is doing much better, destroying those vials before we had a chance to discuss it further, on top of what he's already pulled, but the worst Krouse has done thus far is lie \emph{by omission}.  You lied to my face.  Said you were looking for something to help transport Noelle.''



``I'm willing to bite the bullet,'' Cody said.  ``I'll take the hit.  I'll drink the stuff, or inject it, whatever.  And if the Simurgh has things set up so I get fucked over down the road, I'm okay with that.  I can still use whatever powers I get to get us out of here.  Maybe get us home.''



``Get us home?'' Krouse asked, ``Like it's that easy.''



``Everything comes down to \emph{money},'' Cody said.  ``Think about it.  We get a few million bucks, pay one of those mad scientist types, and they get us home.  Maybe I die or something in a few months or a few years.  But I'm not staying here!  I'm not putting up with this \emph{fucking} dynamic!''



Krouse noted Marissa coming in through the front hall, standing behind him.



``What dynamic?'' Luke asked.



``The one where \emph{he} comes out on top!  Where everyone else is okay with the shit he pulls and then pats him on the back when that shit works out in everyone's favor!''



``The Simurgh fucked with your head,'' Krouse said.



``No!  This has been bothering me for a \emph{long} time!''



``Listen!'' Krouse raised his voice.  Cody glared, but didn't speak.  Krouse continued, ``She fucked with your head, brought that simmer to a boil.  She wanted this.  She wanted Luke and Noelle and Oliver to be distracted, that's why she made them remember the things they did.  She wanted you to hate me, and I think she wanted\emph{ me} to go just a little too far.''



``Krouse,'' Luke said, his tone a warning.



Krouse's tone was matter of fact, calm.  ``I will.  I'll admit it, I'm a crummy person and Noelle seems to like me anyways.  You have no conception of how major that is, or of the hurdles we've had to get past to get even this far in our relationship.  So yeah, I'll go too far if I'm pushed, right here, right now, because I have to protect Noelle.''



Cody folded his arms.



Krouse continued, ``It's probably what the Simurgh wanted, maybe even why she made me as reckless and violent as I was when we ran into those supervillains.  So I'd cross that line \emph{once}.  She set me up so I'd do it, like she's set you up so your resentment's at a fever pitch.  If you attack me, I'll probably kill you.''



``You're talking out your ass,'' Cody snarled the words.



``I'm done with you,'' Krouse said.  ``You can't let go of shit, can't see far enough past what's between the two of us to know how shortsighted you're being.  Our situation right now?  We've got \emph{priorities}.  Noelle is number one, but the rest of these guys come in a close second.  So I'm going to go help Noelle and get her into the car I brought, and we'll get her and Luke to a hospital.''



Cody only glared.



``And Cody?  If she suffers at all because you wasted time, then I'm going to make \emph{you} answer for it.''



Krouse turned his back on the guy, making his way to the living room.



``Need help?''  Marissa was on his heels.



``Help Jess.  I can carry Noelle, and I want to be out of here sooner than later.''



``Okay.''



``Luke?'' Krouse said, ``Want to use my shoulder to steady yourself?''



``I can use Oliver.''



Krouse nodded.



One by one, they made their way to the cars Krouse and Marissa had brought.  It took time to get Noelle settled in with blankets around her.  Even a little cold left her whimpering and moaning, struggling with less strength than a baby might have offered.  Her eyes never opened, and she couldn't even lift her arms beneath the blankets, after they were in place.



All the while, Cody stood in the doorway of the house, staring.



It was only after Krouse and Marissa had pulled away that Cody made his way to his car and followed.



\sectionbreak



``Need help!'' Krouse shouted, as he pushed the hospital doors open with his foot.  Noelle was in his arms.



There were only twenty or so people present.  No staff.  Plastic panels had been boarded up so that they blocked half of the access hallways.  The front desk, too, was similarly blocked off.  A camera sat on the desk, pointing forward.



Krouse went out of his way to avoid putting himself in front of the camera.  He banged on the plastic panel that hung over the front desk's window.  ``\emph{Hey!  }This girl is dying!''



``\emph{Please wait},''  a voice said.  It sounded over an intercom or something.



``She's waited \emph{way} too long already!''



``\emph{Stay calm and be patient.  The staff at this facility are strictly limited to the volunteers who were willing to undergo the quarantine procedure themselves.  As such, this facility is currently understaffed.}``



Was it an automated message?  No.  He didn't get that vibe.



``Sit, Krouse,'' Marissa said.



Krouse settled Noelle into a chair, then sat beside her.  ``Fucking creepy.  I think that thing in the booth is an artificial intelligence.''



``No shit?'' Luke asked.



``No shit,'' Krouse said, his leg bouncing up and down restlessly.  It had to have been at least eight hours since the initial injury, but the minutes that were passing now that help was so close were a special kind of torture.  He studiously ignored Cody, who was standing on the other side of the waiting room.



The others in the waiting room included two nuclear families, a collection of older people who might have come from an old folks home and five men in protective gear that looked like what a firefighter might use, but they had the word `Rescue' emblazoned across their shoulders.



``We get asked about where we came from,'' Krouse murmured to the others, ``We stick as close to reality as we can, but we don't name people or places.  Better to look dumb than name a place that doesn't exist.  Any tips, Jess?''



``Nine-eleven didn't happen here.  Endbringers did.  They have one dollar coins in this America, not bills, and they phased pennies out.  Um.  There's an installation on the moon, half-built and abandoned.  I don't know.  \emph{Stuff} is different.''



``Is any of this even liable to come up?'' Luke asked.



``Don't know.  Better to be safe,'' Krouse said.



Two people in nurse's uniforms hurried out of the mouth of the hallway.  One, a man, approached Krouse and his friends.  Krouse stood from his seat.



``Situation?'' the nurse asked.



``Two moderate injuries, one severe,'' Krouse said.



``She's the severe one?'' the nurse asked.



``Yeah.  Stuff fell on her.  Her stomach's turning black.''



``We'll look after her,'' he said.  He whistled.  ``Esme!  Stretcher!''



The other nurse ran to get one.



``Only six of us volunteered,'' he said.  ``Lots of rules, lots of drawbacks, when it comes to the quarantine.  We were on the outside, but we get treated same as you for coming in.  Can't blame others for not being willing to make the sacrifice, but it's tough with the limited staff.  Who else is injured?''



``Impaled hand,'' Krouse raised one hand.  He pointed at Luke.  ``And sliced leg.  If you're going by priority, put me last.''



``Not critical?''



``No,'' Krouse said.  He looked at Luke, ``No, right?''



``I'm okay for now,'' Luke said.



The other nurse had arrived with a stretcher.  The pair checked Noelle over, then loaded her onto it.  She disappeared down one hallway



Krouse sank into his seat.  It was out of his hands now.  He could finally let himself relax just a little, finally-



\emph{``Sir?''}



It was the intercom by the camera.



Hesitant, he stood, then he stepped closer, still avoiding the camera.



\emph{``Please take these papers and distribute them to your companions.''}



Krouse took the stack of paper.  They were stacked together in packs of six.



\emph{``Be informed, individuals within the quarantine area must meet the prerequisites noted on those sheets before they can be permitted to process out and re-enter society. Under the D.D.I.D. measures, individuals found to be circumventing the listed procedures and strictures or violating the post-release conditions will be criminally charged.''}



``What?''



\emph{``Do you require further explanation of the D.D.I.D. measures?''}



``What measures?''



\emph{``To be processed out of the quarantine area, individuals are required to undergo ten months of twice-weekly checkups with a rotating body of quarantine processing agents.  Eight of those months will also involve weekly sessions of counseling and psychiatric evaluation.''}



``Ten months?''



``Ten months, correct.  Further, anyone processing out of quarantine is required to accept a tattoo marking their D.D.I.D. status.  Each such individual will be placed on a list, with twice-weekly checkups with quarantine processing agents continuing indefinitely.  Attendance at any official or non-official function with more than ten individuals present requires permission from a quarantine processing agent, a minimum of forty-eight hours in advance.  The individual in charge of the function should be notified \emph{of your D.D.I.D. status} upon your arrival.  Any employers should be notified of your D.D.I.D. status at the first opportunity.  Anyone selling or renting property to you should be notified of your D.D.I.D. status at the first opportunity.  Financial institutions should--''



``Stop.''



\emph{``The remainder of details are noted on the sheets provided.  This counter can answer any further questions.  The operator overseeing the quarantine area can answer any further questions.  As noted on the sheet, the operator can be contacted--''}



``Stop.  Shut up,'' Krouse said.



The mechanical voice went silent.



Krouse turned to leave.



\emph{``Sir?  There is one other matter to discuss.''}



Krouse turned back.  ``What?''



\emph{``Regarding the care of the young woman, will you be paying the balance?''}



``I don't have any money.''



\emph{``Understood.  If you will provide the name of your financial institution--''}



\emph{My financial institution\ldots a world away.}



It dawned on Krouse, belatedly, that he was a person without an identity.  His driver's license, his banking info, his birth certificate\ldots they didn't count for anything here.



``Why?''  Krouse interrupted it.  ``Can't you guys pay for it?''



\emph{``Of course.  You will be reimbursed for costs incurred in the course of your processing.  But the process will be expedited if you pay now.  Failure to do so could mean additional delays.''}



``That's ridiculous,'' Krouse said.  He thought of the credit card he'd taken from the drawer. If he used that\ldots  No.  Too dangerous.  But there had been any number of stores that had been left abandoned.  ``I can pay cash, if given a chance to go collect it.''



\emph{``These measures were put in place to ensure that we are able to track anyone undergoing quarantine processing, as well as those who may be attempting to circumvent processing.  We will require a credit card or a bank account number.''}



``If I don't?'' he asked.  ``My stuff got destroyed in the attack.''



\emph{``Again, we can contact your financial institution on your behalf and start the process of restoring your accounts to your control.  If you do not pay, you will not be processed.''}



``And my girlfriend?''



\emph{``The patient will not be processed, either.''}



``If I say I don't have the money, and I can't pay her fee?''



\emph{``We will request financial information from the patient at the first opportunity.''}



Noelle, Krouse was almost certain, didn't have a wallet on her.  No, they'd left her purse in Luke's apartment, and that was in shambles.



``If \emph{she} can't pay?''



\emph{``We will attempt to contact her financial institution.''}



``If you can't?''  He searched for an excuse, ``She was confused, before she went unconscious.  She might have hit her head.  If I can't give you that information and \emph{she} can't give it to you, what then?''



\emph{``Then the department will pay.  But quarantine processing will not continue until you have provided identification and financial information to verify your identity.''}



Krouse returned to his seat, set his hands on his head.



\emph{Fuck you, Simurgh}, he thought.  \emph{Fuck you and fuck this foreign Earth.}



``Krouse?''  Marissa asked.  ``Was it about Noelle?''



\emph{She's forcing our hands.}



``Quarantine measures,'' he said.  He shoved the papers at her, half-crumpled in his hand.



She took them with a gentle touch that stood in stark contrast to the force he'd just used, as if afraid to provoke him further.



``What do you mean?'' Luke asked.



Krouse spoke in a low voice, ``I mean we don't get out of this quarantine area without I.D. and bank info, which we don't have, and even then, we get treated like criminals for the rest of our lives.''



``There's got to be a way around it.''



``No.  I don't think there are.  They're on the watch for that stuff.  For anyone trying to slip past the system.  So we either need to take \emph{ten months} to process out of here, with enough psychiatric counseling and talks with quarantine officers that we're bound to slip up somewhere, \emph{and} we'd have to get flawless I.D. that's going to meet the standards for their checks--''



``Which is impossible,'' Cody said.  He'd approached and was listening.



Krouse nodded.  ``--\emph{and} we'd get treated like criminals for the rest of our lives, or we take option two, we try to escape, and again, we get treated like criminals for the rest of our lives, only we deserve it.''



Another family came in the front doors, finding chairs to settle into.  Two twenty-somethings and two people who looked more like grandparents than parents.  They were sitting close enough that Krouse couldn't continue risk being overheard.



He fell silent, and the others read the papers detailing the quarantine protocols.



It was two hours before the male nurse returned to the lobby with news about Noelle.



Krouse didn't even finish listening before dashing for the door.



\sectionbreak



``Well played,'' Krouse said, as the car skidded to a stop outside the house they'd borrowed.  ``Well fucking played, Simurgh.''



He stepped out of the car.



\emph{Permanent damage.  Removing the majority of her lower intestine.}



He didn't step into the house they'd borrowed.  He headed straight for the house next door, the one they'd broken into when they were looking for house keys.



\emph{Interrupted blood flow, infection, possible signs of necrosis.  She'll require a colostomy bag even in the best case scenario. In the worst case scenario, well, there's any number of ways this could end badly for the patient}.



\emph{End badly}, Krouse thought.  \emph{She'll die.}



Heading inside through the side door, he locked it behind him and made his way to the living room.  The canisters were sitting under the couch, along with the papers.  He flipped through them.


\begin{description}
    \item{\strong{Canister A:}} F-1-6-1-1, \emph{`Deus', }85\% mixture.
    \\  Added: C-0-0-7-2, `Balance', 15\% mixture.
    \\  {\hfill \emph{To be consumed by Client 1}}

    \item[\strong{Canister B:}]  R-0-9-3-6, `Jaunt', 70\% mixture.
    \\ Added: C-0-0-7-2, `Balance', 30\% mixture.
    \\  {\hfill \emph{To be consumed by Client 2}}

    \item[\strong{Canister C:}] C-2-0-6-2, `Prince', 55\% mixture.
    \\  Added: O-0-1-2-1, `Aegis', 30\% mixture.
    \\  Added: C-0-0-7-2, `Balance', 15\% mixture.
    \\  {\hfill \emph{To be consumed by Client 3}}
    
    \item[\strong{Canister D:}] M-0-0-4-2, `Vestige', 75\% mixture.
    \\  Added: C-0-0-7-2, `Balance', 25\% mixture
    \\  {\hfill \emph{To be consumed by Client 4}}

    \item[\strong{Canister E:}] X-0-7-9-6, `Division', 80\% mixture.
    \\  Added: C-0-0-7-2, `Balance', 20\% mixture
    \\  {\hfill \emph{To be consumed by Client 5}}
    
    \item[\strong{Canister F:}] E-0-7-1-2, `Robin', 60\% mixture.
    \\  Added: C-0-0-7-2, `Balance', 40\% mixture
    \\  {\hfill \emph{To be consumed by Client 6}}
\end{description}


``Can't even say what they do, huh?'' he asked.  ``Because you want to leave maximum room for us to screw up, is that right?''



He could hear a car on the road, the crunch of heavy snow beneath tires.  A car door slammed.  He flipped back several pages to reread the directions.  Nothing more complicated than drinking the stuff.



\emph{But which one?}  He stared at the list, muttered, ``Jaunt.''



A small laugh escaped his lips.  Didn't a jaunt mean a short trip?



``Well, that's as fitting a choice as any,'' he said.  He could hear the others making their way inside.



He screwed off the top of the canister and withdrew the vial inside.  ``A toast!  If I'm screwed no matter which path I take, then at least I'll go forward with courage!  Fuck you, Simurgh!''



Marissa and Oliver appeared at the entrance to the living room just in time to see him tossing the contents of the vial back.  They rushed forward to stop him and only succeeded in catching him as he fell.



Pain.



It was like cold electricity, moving through his body at a speed of an inch a second.



He saw fragmented images, faded, blurry.  A crystal formation, growing in fast motion.  Two crystals, each somehow alive.  They moved by creating more of themselves, letting the crystal behind them die.  He sensed that \emph{years} were passing, but they moved together, insistent.



The second they made contact, the entire world was turned to crystal in a heartbeat.



Another heartbeat later, the world shattered.



Another image.  Creatures that folded and unfolded through space, existing in multiple worlds simultaneously, too many to count, spreading out from the remains of a world.



A third scene.  Falling towards a barren planet, seeing the descent with countless eyes that weren't quite \emph{eyes}.  And a fragment of an idea\ldots that the world had the same general shape as \emph{Earth}.  Landmasses in the right place, if not quite the right shape.  No water\ldots but still \emph{Earth}.



``Krouse,'' Marissa whispered.



``All good,'' he smiled.  He struggled to his feet, then nearly lost his balance.  He had to put one hand on Marissa's shoulder to keep from falling to the ground.  ``It's all good.''



``\emph{Why}?''



``Because I'm brave and stupid and because she's the only one who ever gave me the benefit of a doubt,'' he said.  He tried to walk and fell.  Marissa caught him.



``You can't,'' she said.



``Can too.  `Cause I'm pretty sure it worked.  Not sure how.  But it worked.''



He felt a pressure behind him.  A matching pressure to his right.  He turned to look, to see what was happening, and only saw the flatscreen television and a heavy speaker poised on the edge of the bookshelf.  There was a chord, as if a string stretched between them, vibrating, and the television was suddenly sitting on the bookshelf, the speaker in the midst of the entertainment center.  The television fell with a crash, and the remains of the screen danced across the floor.  Marissa shrieked.



``See?'' he smiled.



``Krouse--''



He was aware of the pressure, aware of the \emph{reaching}.  He tried to push it to move, like he'd move his hand, and it did.  He couldn't exactly feel the shape, but had a sense of the \emph{heft} of the thing he was pressing against.  He pressed the other presence against the coffee table, but didn't feel the same chord.



Could expand and contract it, he noted, as if he were opening or closing his hand.  He tried expanding one.  No, that made it worse.  Expanding the one around the coffee table, grabbing, what, air?



The chord.



The desk from the front hall crashed to the ground and tipped over just beside them.  The coffee table settled in the front hall.  Again, Marissa made a noise of alarm, a yelp.  ``Krouse!  Stop!''



``It's all good,'' he repeated himself.  ``Because I'm going to help her.  Fuck the Simurgh.  Fuck destiny.''



He stopped when he saw Cody in the hallway.



``They'll accept this too,'' Cody said, ``Our friends, \emph{your} friends really, they'll let it slide, won't they?  I get threatened, treated like shit, and you?  Well, you get the breaks.''



``Pretty much,'' Krouse said.  ``But if it helps, you're doing it for \emph{you}.  I'm doing it for \emph{her}.  For Noelle.  Because I love that girl, and she puts up with me, and I'll probably never find another person like that again.  Not in our world and not in \emph{this} one.''



``You're not capable of love,'' Cody said.



``We'll agree to disagree.''  Krouse pushed the presence against Cody, surrounded himself.  \emph{No, not quite.  I'm smaller.  Need to suck in some air\ldots}



They swapped places in a flash.  Cody staggered.



Krouse nearly fell, too.  He caught the rails of the stairwell to balance, grit his teeth in the anticipation of pain.



No pain.  He clenched his bad hand, the one that had been impaled.



It was healed.



``All good,'' he said, knowing he was saying the same thing over and over, rambling.  ``Guess I'll need one for her.''



He grabbed the heaviest book from the coffee table, then reached for a canister\ldots



He could feel it, but couldn't get a lock.  He turned around, looked.



\emph{There.}



The book was replaced by the canister the second he made eye contact.  He nearly dropped it.



Krouse smiled.  ``Not too difficult.  Not hard.''



He whirled around, nearly lost his balance.  ``Well, I'll meet you guys at the hospital.''



``Krouse!''  Marissa shouted.  She stepped forward, reaching for him.  He pushed his power into her and Oliver, switched them so that Oliver was within a few feet of him.



Oliver backed away, scared.  Krouse had expected as much.



``Hypocrite!''  Cody shouted.



``I know this is shitty,'' Krouse admitted.  ``And my excuses, my reasons for doing it, maybe they don't make up for what I'm doing.  But I'm okay with you guys hating me if it means helping Noelle.''



He headed outside, stepping through the side door, glanced around.



The garage of the house he'd just left was still open from where they'd investigated.  It had a car sitting inside.  He smirked.



He had to wait until he had both Marissa's car and the one in the garage in sight before he could lock on to both.  He pushed his presence into each, didn't find it particularly difficult to get a hold\ldots



They switched.  Marissa's car made a crashing sound as it settled in the garage.



He got in his car, then pulled it into the driveway, just in front of the garage.  Cody was just stepping out of the side door.  Krouse saluted him.



Then he swapped himself and his car with the one that was now on the street.



They didn't have keys to that car that was now blocking the driveway.  It would buy him time.



He shifted gears and drove.



\sectionbreak



``Hey, No'.'' He said.  He sat down beside Noelle's bed.



She opened her eyes, smiled just a little.



He smiled back.  ``You're finally awake.''



``Morphine helped.  Hurt too much to even open my eyes, before.''



``Sorry.''



``Hey, Krouse\ldots things are pretty fucked, aren't they?''



``Yeah,'' he said.  He smiled a little.  ``So you caught some of what we were talking about?''



She nodded slowly.  She closed her eyes with such languidness he thought she was falling asleep, but it was only a slow-motion blink.



``Yeah, things are supremely fucked,'' he said.



She nodded a little.  ``I'm due for another surgery.  They gave me one short one, and now they're replacing my blood, see?''



``I see,'' he said, eyeing the blood bags.



``\ldots{}I kind of wish we'd done more boyfriend and girlfriend stuff,'' she said.  ``Sorry.''



``Don't need to apologize.  You did what you had to.''



``I could die,'' she said.  Her voice was feeble, quiet.  ``They're cutting too much out, and they can't wait any longer, but my condition's bad, so I could die on the table.''



``You're \emph{not} going to die.''



``And even if I live, I'm gonna be ugly.  Nice big plastic plug in my belly, with a bag of shit attached.  Which is really ironic, you don't even know\ldots'' she trailed off.



``I sort of figured it out,'' he said.



She nodded.  ``Big scars, bag of shit.  Is why I wish we'd done more, before.  Won't be any good to look at, after.''



``I don't care about scars.  But it doesn't matter anyways.  You're not going to die, and you \emph{won't} have scars.  Or a colostomy bag.''



She turned his way.



He asked, ``You catch any of what we were talking about?  Back at the house?''



``Only some.  Um.  I can't distinguish the reality from the delirium dreams.''



``I suspect the delirium dreams made a little more sense, if that helps,'' he said.



He set the canister down on the short table beside the bed.



``What's that?''  Her eyes widened.  ``That wasn't a dream, then.  Krouse, \emph{no}.''



``\emph{Yes}.  You're going to take this, and it'll help.  You'll live, and you won't need surgery.  Then I'll get you out of here, and we'll go \emph{home}.  Somehow.''



``I don't- no, Krouse.  People were saying\ldots  They were scared.  This\ldots this isn't some minor thing.''



``No.  It's big.  It's huge.''



``There were only six,'' she said.  ``And there's seven of us.''



``You deserve special treatment, after what you've been through.  And I want to make sure you get better.''



``No.  It's\ldots it wouldn't be fair to the others.''



``Screw the others.  Cody, at least, can go fuck himself,'' Krouse said.



``No, Krouse.  I\ldots there's too many things, too many warnings, and stuff you guys were saying about poison-``



He could hear footsteps in the hall.



``What if you take half, then?'' he asked.  ``Only half.  It'll be fair to the others.''



He drew the vial, then found a paper cup by the sink.  He poured half into the cup.



``See?''  He handed her the glass vial



``Krouse-``



\emph{Someone's going to come in any second now}.



``It'll work,'' he said.



``And if it doesn't?  Or if that horrible stuff you guys were talking about comes true?  The\ldots what did you call it?  The cause and effect?''



``If it happens,'' Krouse said, ``Blame me.''



``I don't-``



``Please,'' he said, the word barely above a whisper.  He hadn't realized he was saying it out loud before the word had left his mouth.



She gave him a small nod, and he helped her to drink.



\emph{I'll take the blame.  I'm okay with being the bad guy}, he thought.  \emph{Just so long as you get to live}.





