





Noelle screamed, her back arching.



``Well,'' Krouse said, as he reached for the tubing that led from the bag of blood to her arm.  He pulled it out, then removed the tape that had held it in place. ``That's bound to get someone's attention.''



The heart monitor was erratically shifting from a series of fast beeps to flatlines.  His own heart skipped a few beats until he realized that it wasn't flatlining \emph{for good}.  A steady blare marked an alarm going off.



He stood and blocked the door of the room with the chair he'd been sitting on.  Noelle screamed again, a howl, almost ragged.



Had he screamed that much?  Or taken that long?  He felt a twinge of anxiety.



Someone shoved against the door of the room, but the chair held fast.



Krouse wasn't too worried.  He had his power, so if it came down to it, it was merely a question of-



A landscape stretched around him.  It was a smaller planet than Earth, he sensed, to the point that the curvature of the planet was noticeable as he looked over towards the horizons.  He realized he was looking at multiple horizons simultaneously.  They weren't his senses.



Even with the world being smaller, he shouldn't have been able to see the horizon.  Not unless these senses he was using were more refined, or the atmosphere was thinner.  Somehow things were degraded, blurred around the edges, but it didn't impact his ability to see, only to draw together a complete mental picture.  A film reel with the damaged frames removed, only it wasn't a sequential reel.  There was depth, in more ways than one.



He could focus on the ground, note how craggy it was.  Where the larger expanses of landmass had pressed together, it had cracked and separated in dramatic ways.  The compressed soil of gravel and rocky material formed zig-zagging cliffs and deep chasms.



He could focus on the grove of crystalline figures.  They were more like stalagmites than people, glassy, and the planet rotated thrice in the time it took them to move a discernable distance.  Still, they were \emph{communicating}, vibrating with subsonic hums that played off of the others, complicated ideas.



He tried to discern the hum, but ran into the degradation, the distortion of the frames that had been spliced together, for lack of a better term.  He was jarred into the next available scene.  Two crystalline figures, moving steadily towards one another.



He could tell how they were different from the others.  They were bigger, and they traversed ground that didn't bear the clusters of `dead' crystal that the others left in their wake like a slug's moist slime.  They weren't restricted to the equator where things were hottest.



They closed the distance between them, made contact-



\emph{I've seen this before.  From another angle.  It's a replay.}



No time had passed, but he was dazed, caught off guard as the chair's legs skidded on the tile.  It fell to the ground and the door swung wide open.  A man in uniform charged into the room.  The butt of a rifle caught Krouse in the stomach, and he collapsed.



``What the hell are you doing!?'' the uniform screamed at him.



Krouse coughed and groaned as his stomach rebelled against the violence.  His eyes and his power roving across his surroundings.  Something he could swap for the uniformed officer or for the gun.  With his eyes, he eyeballed mass, eyeballed size and likely volume, tried to match it to what he was feeling from the gun or the officer.



The officer kicked him.



Swap the lamp for the gun?  No, the lamp was too lightweight.



He resolved to switch himself and the officer, grabbing air to compensate for the volume.  The difference was larger than it was with him and Cody, it required extra seconds.



He grunted as the officer kicked him again.



He had a grip.  He winced as a kick caught him in the side of the head, closed his eyes-



Again, he was somewhere else.  He saw energy condensing, two figures intertwining, and the summary birth of countless entities, as if from the birth of a star, only they were \emph{alive}.



\emph{No}, he thought.  \emph{Need to focus}.  This is because of \emph{Noelle.  I'm getting caught up in whatever's affecting her.  A sympathetic reaction}.



He forced himself to look away, tried to focus on his power, instead.



Nothing.  His body wasn't there.



He struggled further, tried to banish the visions, to focus on the empty void rather than the countless creatures that were radiating out from the detonation.



The vision chose its own time to end.  That was the downside.  The upside was that he wasn't quite so disoriented when he came crashing back down to reality.



His power still had a grip on the man in uniform.  Krouse forced a swap.



It didn't change the situation much.  He was still lying on the ground, the uniform still standing, but Krouse was now behind his opponent.



The confusion the teleportation had generated bought him a second.  He got on his hands and knees and then threw himself at the man's legs, driving his side and his shoulder into the back of the knees.



The officer fell, and Krouse hurried to his feet.



The gun was a problem, and he hadn't seen anything he could swap for it.  Everything in the hospital was either too lightweight, too miniscule, or both.



Noelle screamed.



\emph{This is taking longer than mine did}.



Krouse rolled over to grab for the gun.  He only succeeded in getting a grip on it, but he couldn't wrest it from the uniformed man's arms.



The alarm continued to blare, the heart monitor seizing up as it ranged from high intensity to ominous low beeps, and Krouse was losing his wrestling match over the gun.  He knew if he lost it, he'd probably get shot.  The use of his power had been the only way to avoid being beaten into unconsciousness, but he suspected it also raised the stakes.  Given a chance, the officer would kill him in self defense.



The man was pulling with such force that his face contorted into a sneer of muscle strain.  Krouse wasn't so strong, nor quite so tenacious.  He felt the gun slipping from his fingers, felt himself reaching the point where the pain in his hands was overcoming his desire to keep the man from getting the rifle.  He knew he'd get shot if it happened, or struck in the head with the butt-end of the weapon, but the pain\ldots



He reached out, and he found something.  He wasn't thinking in the right terms.  Was still thinking too much about \emph{shape} and not about mass.  The heavy wool blanket that was draped over Noelle had roughly the same mass as the gun.



But he had to be looking at both to swap them.  Krouse let the gun go, backed away as rapidly as he could as he got to his feet.  The uniform was standing, moving his hands to get a grip on the trigger and barrel-



-And the gun was gone, replaced by a blanket.  Krouse tackled his unarmed opponent, knocking him to the ground, grabbing at his wrists.



Krouse closed his eyes and slammed his forehead into the lower half of the uniformed man's face.  He headbutted the guy once more.  Blood welled on his own forehead, where a tooth bit too deep into the skin.  His opponent got one hand free, punched Krouse in the ribs, three times in quick succession, each blow stronger than Krouse might have expected.



\emph{I'm going to lose this fight}.



Using his power to get a sense for where it was, Krouse reached over to the gun, got a grip on the rifle and swung the end of it into the uniformed man's face.  He kept swinging until the officer stopped putting up a fight.



He managed to climb to his feet, blinked slowly as he looked down at the uniformed man. Not a cop, not a soldier, something else.  The guy's face was a mess of blood, and his gaping mouth had at least two broken or missing teeth.



There were nurses and doctors in the hallway, staring.  Krouse stepped towards the door, and they ran.



Noelle was still struggling, thrashing.



``Come on, Noelle,'' he whispered.  ``Best thing you can do for me is stay alive, here.  Don't let this be where I accidentally kill you.  Can't live with that.''



He paused.  There were other footsteps coming down the hallway.



``And if it's not asking too much, hurry it up some?''



When he'd disconnected from reality and seen whatever he saw in the visions, how much had he seen?  Was she halfway done, only a tenth of the way?



Krouse moved the chair to block the door, then dragged the man he'd bludgeoned into place so the unconscious body would keep the chair in place and the door closed.



``Come on,'' he said.  ``Come on\ldots''



For the third time, he found himself someplace else.  All of the memories and thoughts of the hospital room and Noelle thrashing receded as he found himself plummeting, felt the heat of entering the atmosphere, and didn't care in the slightest.  Emotion didn't factor in, from this perspective.



A waterless, lifeless earth loomed beneath him, stretched out until it consumed his senses.



The impact didn't hurt any more than the atmospheric entry had.



-And he was back in the hospital room.  He staggered, nearly fell, but managed to keep his balance.



``How much more, Noelle?'



She was panting, not screaming, sweat beading her brow.



``I\ldots I'm\ldots I think it's over,'' she said.  Her voice was stronger.



``Feel better\emph{?'}



She touched her stomach, pushed herself to a sitting position with her arms.  Her eyes widened.  ``\emph{Yes}.''



Krouse felt a smile stretch across his face, so broad it hurt.  ``Fantastic.  Feel \emph{different}?''



``No\ldots not really.''



``Well, you only got half a dose.  If you get any powers, they're liable to be pretty weak.  Could be that you burned up whatever juice is in that stuff, healing the damage.''



``Maybe.''  She touched the hospital gown.



Krouse looked away, feeling somehow abashed.  ``You'll want to get dressed.  I saw your stuff in the cupboard, with the sheets.''



He found the half-full cup and tipped the contents into the vial, then slid the vial into the canister.  As Noelle climbed out of the bed, Krouse turned his back to her to give her privacy, screwing on the cap and closing the canister with the remaining formula.



Someone banged on the door, hard.



``There's more of these guys.  Thought the process would be faster,'' Krouse said.



``Can we get away?''



``Depends on how much backup they get.  The more the better.''



``Don't you mean-''



``Nope,'' Krouse said.  ``Best case scenario, they'll have tons of backup.''



``I\ldots my bare skin's fizzing.''



``Fizzing?''



``I can't see it, but I feel like there's bubbles, and they're so tiny I can't see them, but they're flowing \emph{down} from my skin.''



``Huh.  You can't control it?''



``No.  Or\ldots sort of?  If I concentrate, pull on my skin, it speeds up.''



Fizzing and pulling on her skin.  It wasn't the most apt description, but Krouse wasn't sure he'd be able to accurately describe the pressure or the feeling of \emph{heft} he got when he pressed his power into something.



``Does it feel different when you touch stuff?''



``Yeah.  Feels like my skin's fizzing against my clothes, as I'm putting them on, where the cloth touches me.''



``Touch other stuff.  If we can figure out your power, maybe we can use it.''



There was a pause.  Krouse waited while she experimented.



The door banged.  He tensed.  This time, at least, he'd be ready.



``Not much.  Less than from my clothes.''



There was another bang on the door.  The chair shifted, and Krouse moved it back.



``Worry about it later.  We're stuck with just my power until we figure yours out.''



Noelle entered his field of vision, wearing all of her winter stuff.



Krouse stepped over to the window.  The street was lit only by the minimal moonlight that filtered through the clouds.  There were police cars and fire trucks massing inside the quarantine area, as well as black vans with pale purple stripes and the letters P.R.T. on the sides.  The people outside the black vans had uniforms like the man he'd just beat up, only they wore helmets.



There were capes, too.  Krouse could see the one with the brown cloak and staff.  Myrddin.  A half dozen superheroes clustered around him.  His team?  It was a surprise that so many heroes were still present in the city.  Did they have to undergo their own kind of quarantine processing as well?



\emph{Doing this all backwards, deciding on a strategy before I've fully tested my powers.  Don't even know my own range}.



Krouse pushed his power away from himself, reached for two of the men in the P.R.T. uniforms, each on opposite sides of the crowd.



They swapped places.  He couldn't really see the physical differences between them, but they were alarmed, confused.



``I can swap us out with someone in the crowd, if it comes down to it.  Happen to know anything about Myrddin?  Maybe Jess said something?''



Noelle shook her head.



``Fuck.  And we have even less chance of knowing something about his subordinates.  Far as I know, he does something with these dimensions he carts around.  When I ran into him, he sort of banished me into this phase state where I could move around and stuff, but I couldn't touch anything either.''



Noelle nodded.



``He didn't mean to, though.  He thought I'd pop back in like I'd just left.  His power, it doesn't work well if something's changed between dimensions too much.  Which means it won't work a hundred percent right with us.''



``Would he listen if we talked to him?''



Krouse looked outside.



``No.  I don't think we could.  We're on our own.  Just\ldots we just need an opportunity.  Stay close to me.''



Myrddin was flying, now.  Two of his subordinates were advancing as well.  One had a beachball-sized ball of jet black extending a foot away from his splayed hands, crackling with arcs of electricity that were both absolutely black and somehow still \emph{glowing }enough to be seen in the dark.  The other figure was an Asian woman with a painted mask and a giant lantern in her hands.



``We have a fight incoming,'' Krouse said, backing away from the window.



Myrddin waved his staff, and the window shattered.  With another movement of his staff, he plunged down into the room, landing with an audible impact.



Krouse had a better look at the guy:  A brown cloak-and-robe combination that might have been burlap, but with a heavier material beneath.  If the raised metal collar around his neck was any indication, Myrddin was wearing some kind of armor or protective gear beneath the robe.  It should have been heavy, but he wasn't having any apparent difficulty.  His staff was a gnarled stick of dense wood, worn by weather.  The upper half of his face was hidden behind a metal visor that served more to cast his face in shadow than to be actual \emph{armor}.  He sported a thick, well trimmed beard.  Brown, not white.



This wasn't a guy that Krouse could fight hand to hand, and between his armor and his stature, he was too heavy to be swapped with anything that wasn't an appliance.



``Stand down,'' Myrddin ordered.



``I'll pass,'' Krouse replied.  He looked at the injured P.R.T. soldier, ``We've got-''



``Begone,'' Myrddin said, pointing his staff.



The officer vanished in a cloud of mist.



``-A hostage,'' Krouse finished.



Myrddin looked at Noelle, then at Krouse, ``So there's two of you.''



``One of us, two bodies,'' Krouse said.



``What?''  Myrddin's eyes narrowed.



\emph{No clue.  Just confusing matters}.  His eyes flickered to the scene behind Myrddin.  No luck just yet.



The man with the black spheres floating around his hands leaped up to the shattered window.  Krouse could see the Asian woman holding the handle of her lantern as it raised into the air.



``Banish one?'' the man with the spheres asked.



``Already banished their hostage.''



``Want me to grab one to take into custody?''



``Be my guest, Anomaly.''



Anomaly raised one hand, and the sphere floated up until it was level with Krouse's head.



Krouse felt a pull, stepped back and grabbed the footboard of the hospital bed.



The pull increased steadily, intense enough to pull at his hair with the strength of a gale.  Noelle said something Krouse couldn't make out as she began to slide towards the thing.



Myrddin, for his part, didn't budge an inch.  The girl with the lantern held onto the handle with both hands to avoid the suction, setting her feet on the windowsill and perching with a crouch.



Noelle slid, and Krouse caught her with his power.  He found the lantern girl, snagged her-



And Noelle was there, on the windowsill, losing her balance.  The lantern girl slid into the sphere, virtually folded over it as it pulled her tight against its surface.



Noelle caught the side of the shattered window with one hand.  He could see her grimace in pain.



\emph{Shattered glass}.  \emph{Sorry}.



He swapped Noelle for Anomaly, and both she and the lantern girl fell hard to the ground.  Anomaly tipped from the window to the interior of the room.



``Who are you?'' Myrddin asked.



Krouse glanced out the window.  No.  This might go badly before he had a chance to execute their escape.  If he had to teleport to the back of the crowd, they could wind up in a situation where there was no escape.



``Nobody dangerous.''



Myrddin shifted his staff, and Krouse tensed.



Where the staff-tip moved, a thread of blinding light was drawn in the air, loose and loopy, like the light trail from a sparkler.



The light exploded outward with a concussive force, and both Krouse and Noelle were slammed against the walls.  The shape of the trail Myrddin had drawn meant the resulting blast passed over and to either side of his lantern-bearing teammate.  Her clothes were barely ruffled.



\emph{He has personal dimensions he carries around with him}, Krouse theorized.  \emph{And}\emph{each one follows different rules}.  \emph{One holds banished people, maybe that one holds energy or compressed air, and he just needs to open it a crack to let the stuff out.}



``Can you open doors between worlds?'' Krouse asked.



Myrddin went stiff.  ``No.  Are you implying you're one of the creatures from the world \emph{she} opened a door to?''



\emph{She}.  The Simurgh.



``Nah,'' Krouse replied, climbing to his feet.  ``Just wondering.''



``Stay down,'' Myrddin warned.  The hero drew another glowing ribbon into the air, more intricate and convoluted than the former.  Krouse braced himself for the resulting impact.



Then he saw it.  A belated arrival to the party.  A police car coming down the street in the distance, maneuvering to pull in and join the ranks of officers and rescue personnel on site.



Krouse turned his head, trying to catch Noelle and the crowd in the same field of vision.



He swapped her for someone at the back of the crowd.  A moment later, gathering enough air, he swapped himself.



The cold air was like a slap in the face.  He reached for her hand, grabbed it.  This new vantage point let him see the inside of the police car.  He reached for the officer and partner, then swapped again.



Krouse found himself sitting backwards in the driver's seat.  He flipped himself over and, as nonchalantly as he could manage, pulled away, heading deeper into the quarantine area.



\emph{We'll abandon the car as soon as we can, then go back to the house.  Face the music}.



He reached for Noelle's gloved hand and squeezed it, but she didn't smile, didn't show any relief.  She looked troubled.



He realized why.  Her left hand was undamaged where she'd slashed it on the shattered glass of the window.



\blacksquare



They traveled the last leg of the journey to the house on foot.  There were no words exchanged between them, even as minutes passed.



As they approached the house, Krouse was left to wonder which one his friends would be in.  He settled on the first house they'd broken into.



Jess, Luke, Marissa and Oliver were there, arranged in the living room.  It was dark, barely lit.  \emph{Makes sense.  They'll be looking for houses with lights on}.



``Noelle,'' Marissa said, leaping to her feet.  ``You're okay!''



She hurried across the room, reached out to give Noelle a hug, and was stopped.  Noelle had her hands on Marissa's shoulders.



``What's wrong?'' Marissa asked.



``Nothing,'' Noelle said.



``You really did it, Krouse,'' Luke said.  ``I almost didn't believe them.  That you'd be that stupid.''



``Oh, I'm a hell of a lot stupider than that,'' Krouse said.  ``But I saved her.''



``You gave it to her?  The can?''



``Half,'' Krouse said.  He withdrew the canister from his front jacket pocket and switched it with a book on a nearby bookshelf, then threw the book aside.  ``Just enough to heal her.  Save her life.''



``And now you two have superpowers,'' Luke said.  ``You're doing exactly what we said we wouldn't.''



``The Simurgh set it in motion, not really my fault,'' Krouse said.



``That's bullshit,'' Luke replied.  Unlike Cody, he was quiet, and the words almost had more impact as a result.  Krouse wondered, \emph{Is it because he's my friend?  }



``If I hadn't done it, things would have gotten even worse.  If she wants us to use the stuff, then we eventually would have.  It's extortion, extortion through fate, I dunno.  But I chose to pay the price rather than wait for her to ramp things up until I had to.  If you want to blame me, blame me.''



``No fucking shit we're blaming you,'' Luke said, and the hint of anger in his voice wasn't as calm as his earlier words had been.



That anger seemed scarily similar to what Krouse was used to seeing from someone \emph{else}.



``Where's Cody?''



``Here,'' Cody said, from behind Krouse.



Krouse whirled around.



Cody was smiling, swaggering.



``You too?'' Krouse asked, unsurprised.  He'd left Cody in the house with the four remaining vials.



``Yeah.  Me too.''



Everything in the room shifted.  The curtains flickered and appeared in a fractionally different position, Noelle had moved a foot away, now squarely facing them, and Cody was in the center of the room.



``See?'' Cody asked.



``What just happened?''



``I got powers.  The paperwork said it was the `Vestige' can.  And as luck would have it, my power counters yours.  Totally and completely.''



There was another shift, things moving all at once, and Cody was now a foot in front of Krouse.  He was laughing.



Teleportation?  No.  The others wouldn't move like that.



``Stop it, Cody,'' Marissa said.



``He doesn't care, he doesn't know,'' Cody said.



``Just stop!''



Everything shifted positions again, and this time, Cody was swinging a punch at Krouse.  It connected and Krouse crashed to the ground.  The punch had landed painfully close to where Krouse had been struck not long ago, and the resulting pain seemed to radiate across the surface of his skull.



``Only bad part is,'' Cody said, shaking one hand as though it were sore, ``If I use it on myself, I don't get the \emph{satisfaction, }and if I use it on him, he doesn't even know.''



``Just leave him alone,'' Marissa said.



Krouse looked at Noelle, saw her with gloved hands pressed to her mouth.



``What's he doing?'' Krouse asked, not moving from the ground.



``Time travel,'' Luke said.



Cody shrugged, ``Directed time travel, anyways.  Backwards only, a few seconds at a time.  You teleport away, I set you back to where you were, then kick you in the balls for being an asshole.''



``Well,'' Krouse said, ``Do you feel better now?  After however many beatings you just gave me?  Kicks in the balls?''



``I feel a \emph{bit} better.  But what has me tickled is that I can do it again and again, whenever I feel the urge,'' Cody said, smiling.



``Don't,'' Luke said.  ``That's\ldots''



``Brutish,'' Jess said, her voice low.  She was glaring at Krouse.



``Not the word I would have chosen,'' Luke said, ``But yeah.''



Cody shrugged.  He couldn't stop smiling.



``Listen,'' Krouse said, ``Noelle's better and she's safe.  That's priority number one done with.  Now we need to get out of here, and then we focus on getting home.''



``You know, Noelle?''  Marissa asked, ``You know about our situation?''



``Some.''



``Come on then, let's leave the boys to hash this out.  I'll fill you in on what's going on while we get our stuff packed.''



``Food first?'' Noelle asked.  ``I haven't eaten since yesterday.''



Marissa gave her a funny look, but she led the way to the kitchen.



``Stuff?'' Krouse asked the others, when the two girls had left.



The room flickered.



``\emph{Stop}, Cody,'' Jess said.



``I'm tired of everyone catering to him.  He fucked up, broke the rules \emph{he} set,'' Cody said.  ``So if he wants to run off and be the lone maverick, he can deal with the consequences.  That means we \emph{don't} go out of our way to get him caught up.''



``You're being as bad as he ever was,'' Luke said.



Cody turned towards Luke, ``No.  No I'm not.''



``You're making calls on \emph{our} behalf.  You're not being a team player, and you're making things harder than they have to be to get your way.''



``It's not the same,'' Cody said.



Krouse looked at Cody, then grabbed him from behind and threw him into a bookcase.



``Krouse!'' Luke shouted.  Marissa and Noelle hurried back to the hallway.



Cody appeared back where he'd been standing, in the exact same position.  Krouse repeated the throw from behind.  ``Two!''



Again, Cody reappeared, setting himself back to where he'd been three seconds ago.  Krouse shoved him yet again.  ``Three!''



On the next reappearance of Cody, Krouse shoved him and called out, ``Four!  Blade cuts both ways Cody!''



This time, Cody didn't use his power on himself.  He landed amid the fallen stacks of magazines and books, offered a snarling noise.



``Your power works against you,'' Krouse said.  ``Using it to protect yourself?  It doesn't work if your opponent knows how you function and you don't have backup to break the loop.  You shift yourself back in time, you don't remember, and I can use the same strategy over and over.''



``That's not-'' Cody said, then he stopped.  His eyes narrowed.  ``I don't have to put you back where you were after hurting you.  Any time you do something to me, I can set you up to a position where I can hurt you, then leave you like that, hurting.  Using my power doesn't tire me out.  I can set you back as many times in a row as I need to.''



``Just stop,'' Jess pleaded.  ``All of this is hard enough without you two being enemies.''



``Problem is, Jess,'' Krouse said, not breaking eye contact with Cody, ``Cody's got this mindset where the guy with the bigger stick wins. He doesn't care about the big picture until he's established his dominance.  Since idea of dominance is kicking my ass, we can't have him doing that while we're trying to get back home.  It's\ldots counterproductive.''



``Yeah?  What are you going to do about it?'' Cody asked.  He was pulling himself to his feet.



``Nothing,'' Krouse said.  ``You want to pull stunts like that, feel free.''



``Thought so,'' Cody smirked.



``And,'' Krouse said, stepping close enough to whispered in Cody's ear, ``Your power's kind of a liability, you know. Not just the double-edged sword part.''



``Liability?''  Cody asked in a normal speaking volume.



Krouse continued whispering.  ``A liability.  You saw what I was willing to do when the Simurgh forced my hand by putting Noelle's life on the line.  Now my hand's dangerously close to being forced again.  Because I \emph{will} get these people home, and if you get in my way, if you give me reason to fear for my safety or to make me think we aren't making as much progress as I want?  Well, the only way I can think of to shut down your power is by killing you.''



Cody smirked, stepping away.



His eyes flickered across Krouse's face as he read Krouse's expression.  Cody's smile faded.



Cody forced a smile onto his face again, but it didn't seem quite so genuine.  ``I'm going to go pack my shit.  You have my permission to fill the asshole in on the details.''



\emph{You're a coward at heart, }Krouse thought, as he watched Cody head upstairs.  \emph{And I'm too stubborn to back down or give up.  As long as that's the case, I'll always come out ahead.}



He looked at the others, ``Well, I think that's that.  Let's talk about the next step of our plan.''



He seated himself on the couch, flashed Noelle a smile.



Noelle smiled back, but it didn't quite reach her eyes or overcome the concern in her expression.  She turned back towards the kitchen, and Marissa followed.



Krouse's heart sank a little at that.  It felt like they'd somehow been set back weeks or months in their relationship progress.



He distracted himself.  Turning to Luke, he asked, ``What was that about `stuff'?''



``Stuff.  We weren't quite sure where you went, and you kind of made it impossible to get the car out of the driveway,'' Luke said.  ``So we went shopping, so to speak.  Brought back clothes, toiletries, and all the cash we could get out of the registers, pretty much every place within walking distance.  We even got an old wheelchair for Jess, rinsed off the seat in the shower upstairs.  We're just waiting for it to dry off.''



Krouse smiled.  ``Good man.''



Luke wasn't smiling back.  ``It feels shitty, stealing.''



``Nobody's going to touch that money anyways,'' Krouse said.  ``Not with it being in the quarantine area.  That was a smart move, really.  Does this mean we've got everything we need to get by for the next while?''



``Pretty much.  You should go through the stuff we brought and make sure it all fits, and that you aren't going without something essential.''



``You didn't happen to pick up cigarettes?''



Luke frowned, ``I shouldn't have, told myself you didn't deserve it after what you pulled.''



``But?''



``But I did.''



``Best friend!'' Krouse smiled, spreading his arms wide.



Luke shook his head.  ``You don't deserve it.''



``I don't.  But I'll make it up to you by getting us out of here with my power.  Shouldn't be hard; there weren't all that many soldiers outside the fence, and we can swap ourselves for them, maybe.  If Cody cooperates, that makes it even easier.''



``And Noelle?'' Luke asked.  ``Does she have powers?''



``Apparently,'' Krouse said, ``Though I don't have any idea of how it works.  You guys give any consideration to the idea of using the rest of the juice?''



Luke was nodding a little.



``Luke!'' Jess said, aghast.



``What?  Half the damage is already done,'' he said, ``And as far as I'm concerned, the benefits of getting more powers outweighs the possible danger.  We don't have any real income, we don't have anybody to go to for help, and it's going to be \emph{far} easier to get funds if we can do something like mercenary work with a team of people with powers.  Like Cody was talking about, we could hire someone to get us home.''



``I don't think this is a good idea,'' Jess said.



Luke sighed, ``Let's be honest.  If it's just Noelle, Cody and Krouse who have powers, I'm worried things will get ugly.  There's too much tension, but I don't think any of us are willing to leave the group and strike out on our own, not when it means being all alone in a strange world.  So we're stuck together, and that means there's going to be conflict.  If they aren't the only ones with powers, then at least we can do something to stop a fight from erupting.''



``I don't know,'' Jess said, ``I feel like it'll make the problem worse.  And you talk as if being a superpowered mercenary isn't dangerous.  \emph{And} it won't be that \emph{easy} to find a tinker who can give us a way home.''



``There's a thousand mad scientist types in this world, aren't there?  \emph{Someone} knows how to get us back,'' Krouse said.



Jess frowned.



``Jess,'' Luke spoke.  ``\emph{Superpowers.  }And the stuff healed Noelle.  Maybe it'll heal your legs.  Think about it.  Walking, dancing?  Running?  Other stuff, stuff with boys?''



Her expression shifted a fraction.  For the first time since the powers had been brought up, he thought maybe there was a sign of interest.



She looked at Krouse, and Krouse shrugged.  ``We have three and a half vials left.  Someone's going to get only a half dose.''



``You're assuming I take one,'' Jess said.



``I am,'' he echoed her.  ``She set Cody against me, so I had an adversary, putting me off balance.  Then used Noelle's injury to push me to act.  And you guys?  You, Luke, Marissa and Oliver?  She kept you \emph{occupied}.  Kept you focused on yourselves.  You want to talk about the Simurgh's game plan?  It centers around \emph{me}.  I can't see any other way of looking at it.  She isn't aiming to have you guys get mondo powers and kill a president or something.  Why would she make Oliver feel like crap if that was her end goal?''



``It's you?'' Luke asked.



``Doesn't it make sense?  Just look at where the focus is.  She distracted you guys because you were the ones who could have talked sense into me.  The can of worms is opened, and \emph{I'm} the person she's turned into a guided missile.''



``You don't sound too worried for someone who believes that,'' Luke said.



``I'm\ldots I'm processing it,'' Krouse admitted.  ``But that's what it looks like, to me.  And if there isn't anything that points to me being wrong?  Maybe I should just help you guys get home, then stay here.  Become a hermit or something.  Let me keep however much leftover cash we wind up with, and I'll find an apartment and while away the rest of my days watching movies and playing games over the internet, not saying two words to anyone.  Don't know how much damage I could do that way.''



``Or come with us,'' Luke said.  ``There's no way she can see the future of this world \emph{and} ours.  No way she's turned you into some ticking time bomb that's going to fuck \emph{our} world over.''



Krouse shrugged, ``Maybe.  I can decide when we get that far.''



``Three and a half vials,'' Jess said.



Krouse nodded.  \emph{She's on board}.



``You took the Jaunt one and the Division one,'' Luke said.



``Leaving\ldots''



Luke was already getting a piece of paper out of his pocket, unfolding it.  ``Prince, Deus, Robin and half of whichever vial you gave to Noelle.''



``Half of Division,'' Krouse said, ``Funny.  But it doesn't look like Noelle has powers.  She's said her skin fizzes, whatever that means, but maybe it's incomplete\ldots''



``I'll take half,'' Oliver said.



All eyes turned to him.  Oliver continued, ``If Noelle doesn't want to finish it, I'll take half.  I'm not strong, I'm not brave, or smart, or creative.  I don't have it in me to be a hero.  So as long as you don't ask me to risk my life fighting stuff like the Simurgh, I'll take the half, try to find other ways to help.''



``You don't give yourself enough credit,'' Krouse said.  ``You're a decent guy.''



``Maybe,'' Oliver said.  He sounded sad, ``Maybe I'm \emph{decent}.  But I'm not a great guy.  Like I said, nothing about me is special.  Nothing's exceptional.  So I'll take half.''



``Okay,'' Krouse said.  ``Anyone want to call dibs on the others?''



``Robin,'' Luke said.  ``Sounds like it might mean I could fly.''



``Mars?'' Jess asked.  ``You care?''



Marissa shook her head.



``Then Deus for me.''



``That leaves me with Prince,'' Marissa said.  ``I hope it doesn't turn me into a boy.''



``Are they still next door?'' Krouse asked.



Luke nodded.



``We dose you guys one at a time so we can be sure we have everything under control and minimize any damage.  Then we'll leave before sunrise.''



The others nodded.



\blacksquare



The car coasted down the long highway, the windshield wipers clearing away the moisture of the freezing rain.  Krouse pumped the windshield washer fluid and then wiped it away.



Madison was well behind them, now.  Odd, how it felt like he was leaving home, even when it wasn't really his city.  A bad copy, an \emph{ugly }copy.  One with more violence, where the criminals could do far, far worse, by virtue of having more power.  Having \emph{powers}.  That was without even touching on Endbringers, the Simurgh, and the desolate quarantine area.



Cody was in front.  Krouse didn't mind, didn't care about giving up that token alpha-maleness.  If that's all it took for Cody to be satisfied for the time being, he'd accept it.



He'd save his strength for the more serious conflicts.  They \emph{would} happen.



The sun was rising.  It was a bit of a relief.  Driving in the rain and snow, in the dark, with the headlights seeming to extend a scant twenty feet ahead?  It sucked.  The rain continued, and the sky was overcast, but it was transitioning into a beautiful sort of overcast, with dark purples and oranges.



He looked at where Noelle sat in the passenger seat, reached over and squeezed her hand.



She looked at him and smiled a little.  It was better than he'd gotten in the last little while, and the surge of relief he experienced was almost palpable.



Marissa and Jess were in the back seat, either already sleeping or most of the way there.  He'd resisted the urge to comment, to note how the girls were with him, avoiding Cody.  They knew something was off.  That Cody was just a little too aggressive.  A little too testosterone driven.  As far as Krouse was concerned, it said something that the girls felt safer with him, even after everything that had happened.



They had their powers, and there was a slight cast of disappointment for everyone involved.



Jess could walk\ldots but only with the images she projected.  Her real body seemed largely unaffected.  She got to experience everything she'd never had a chance to, even got to \emph{fly}, but at the end of the day, she was still in the chair.



Marissa was managing to create flickers of light between her hands.  She'd stopped when a nearby piece of paper had caught on fire, resolving to try it when there was more open space.



Luke was especially disappointed with his power; it hadn't been flight.  No, it was destructive, singular and without any versatility.  He turned anything he touched into a projectile.  It \emph{would} be useful for mercenary work, if they were willing to take on the more dangerous jobs.  It came down to how long they were willing to wait before they got home, and how much money was demanded of them.



It was the day before Christmas Eve, Krouse remembered.  He'd have to be thankful for their well being, at least.  They were alive.  Things were \emph{okay}.  Not great, but not as hopeless as they might have seemed before.  And things had settled down, at least.  For the first time since the others had joined him and Noelle at the coffee shop to discuss his inclusion on the team, things were \emph{calm}.  They'd find a way to put their new powers to work.  They'd get money, get themselves home.



Things made \emph{sense} again.  Mostly made sense.



Cody's turn signal came on.  He was pulling into a rest stop.  One of the off-the-highway areas with a few fast food places and a gas station.



There weren't many cars on the road, this time of morning, and less in the rest stop parking lot.  Cody pulled in just beside the front door.  Before Krouse was able to pull into another parking spot, Oliver was out of the door, running for the bathroom.



Oliver hadn't changed either.  Half a dose apparently wasn't enough.  It \emph{did} seem to make the aftermath of drinking the stuff worse, though.  Oliver's condition had been nearly as drawn out as Noelle's after he'd taken his dose.



``Anyone need to make water?'' Krouse asked.  ``Fast food places might be open if you're hungry.''



The two girls in the back seat groaned, but they roused.



``Want help with the chair?'' he asked.



``We've got it,'' Noelle said.  She flashed Krouse a small smile and headed inside.



Krouse fished in his pocket for a cigarette, whispered praise to Luke.  He popped it in his mouth and then started looking for the lighter.



Noelle knocked on the windshield, gave him a death glare.



``What?''  He offered her an exaggerated shrug



``Not in the car!'' she admonished, her voice muffled by the intervening windows.



He smiled a little, climbed out of the car, leaned against the door and lit the cigarette.  While he puffed, he stared at the clouds as faint traces of the sunset's colors traced across them.  The rain was freezing cold and irritating, but the cigarette was worth it.



When he'd finished the first and the others hadn't returned, he resigned himself to walking across the parking lot to a spot where there was shelter from the rain, starting on a second cigarette.



He was halfway done when Marissa came outside.  He walked slowly in the direction of the car, taking a deep pull on the cigarette, thinking of how to gracefully point out that the others were taking a long time.  Then he saw her eyes.



She was afraid, white as a sheet, and she was silent in a way that suggested she didn't know what to say.



He ran her way, spitting out the cigarette.  She held the door open for him, and then led the way toward the women's bathroom.



There was a heavyset manager from one of the fast food places just at the door, shouting at Cody in a gruff voice.  Krouse ignored them, headed inside the bathroom, ignoring the manager's shouted protests.



Noelle had crumpled to the ground at the far end of the bathroom.  Oliver, Luke and Jess were huddled around her.  Marissa moved straight to Noelle's side.



``Don't touch me!''  Noelle screamed, her voice shrill.



Marissa stepped away, hands raised, as if showing she were unarmed, \emph{safe}.



``What happened?'' Krouse asked, his voice quiet enough that the others might hear, but Noelle wouldn't.



Each of the others gave him a look, expressions haunted.



He stepped closer, to get a better view.  Noelle's pants were down around her knees.  Her jacket meant Krouse couldn't see anything but her thighs.  There was a mark about a foot long and eight inches wide, raised on her left leg.  Red, angry, it was wrinkled and blistered like a bad burn.



She saw him. moved to try and cover herself, ``Don't look, Krouse!''



He turned to step away, to turn his back, but Jess reached out, caught his pants leg.



He looked again, saw Noelle's head hanging, her hair a curtain around her face.  She was sobbing.



The skin on the angry red mark parted.  There was no surprise from the others; they'd seen this already.



Beneath the angry red skin on Noelle's thigh, there was an eyeball, twice the normal size, with a broad yellow iris.  Noelle's hands were clenched into fists, gripping the cloth of her jeans as the eye's gaze darted from one member of their group to another.  It settled on Krouse.



\emph{Accusatory}.





