





``He'll be one minute,'' the woman at the front desk spoke.



Trickster nodded.



``If you'd like to take a seat\ldots''  The woman trailed off.



``I prefer to stand.''



``As you wish.''



``Can I smoke?''



``No.''



``If I open a window--''



The woman at the desk frowned.  ``My employer is\ldots particular.''



``I've heard.''



``If you leave the cigarette butts lying around, or if this room smells too strongly of smoke after you've left, he will be upset.''



``I understand.''



``It's your funeral,'' she said.



Trickster stepped over to the window, found the latch, and swung it open.  He rested his elbows on it and leaned out, drew a cigarette and lit it, being sure to hold it and exhale outside of the window.



The Boston skyline stretched out before him, with the ocean in the distance.  Over the last year and three months, he'd picked up on how things were subtly different in this world.  It wasn't explicit, wasn't overt, but he couldn't help but notice that all of the newer constructions were sturdier.  Buildings were more reinforced, just a little thicker where supports were required, as though disaster was always at the periphery of the designer's attention.  At the same time, windows were often larger, and many apartments had floor-to-ceiling windows for a wider view of the world beyond.



How had Jess put it?  This world was sublime.  A world that was awesome in the truer sense of the word, \emph{greater} in so many respects.  In a metaphorical sense, the peaks were higher, the valleys lower, works of art more \emph{artful}, extremes more\ldots extreme.  It wasn't a good thing.  \emph{Make the mountains twice as tall and the chasms twice as deep, and things start crumbling}.



He missed home, but every day, every week, home felt a little further away.



``Accord will see you now, Trickster.''



Trickster nodded, crushed his cigarette against the outside of the building, flicked it over the ledge, and then stepped away to close and latch the window before entering the office. He was sure to remove his hat.



Supervillains were \emph{weird}.  Every one of them had different rules, different aesthetics, different goals.  All of them, himself included, had their own issues.



Accord wasn't the most influential figure in Boston.  That was why Trickster had approached him.  He didn't even look like a supervillain.  He looked like a CEO.  Only an ornate mask with curling, overlapping bands of dark metal trimmed in silver marked him as anything more.  His hair was oiled and neatly parted, and his white suit had been brushed clean with immaculate care.  Trickster doubted there was even a fingerprint or a glimmer of tarnish on Accord's silver tie pin.  For all his presence, Accord was barely over five feet in height.



For his part, Trickster had taken care to clean his own clothing and comb his own hair.  It was becoming a ritual, entering a new city.  One typically had to find the meeting place.  Virtually every city with ten or more supervillains had one, a neutral ground for the villains to meet.  He would then find the people in the know, pay some of the money he'd held on to from the last city to get the necessary information on who was who and how they operated, and move on from there.  He'd been briefed thoroughly on Accord.



``Trickster, was it?''



``Yes,'' Trickster stepped forward.  He offered his hand.



Accord shook it, his grip strong.



``What can I do for you?''



``I'm observing formalities.  My team, as you may know, tends to move from location to location, city to city.  It's a bad idea to settle down for any length of time in an area owned by a local power, so I wanted to ask permission first.''



``I see.''



``If you saw fit to grant that permission, I would then ask if you'd let us engage in some minor activity.  Robbing low-level stores, primarily.  Possibly a bank.  All in your area.''



``\emph{If} I granted that permission, Trickster,'' Accord raised a warning finger. ``I would not be doing so for free.''



Trickster nodded.  ``I understand, and I wouldn't expect you to.  We've recently passed through Richmond, Paine, Baltimore and Philadelphia.  Each time, we paid a modest up front fee to anyone that hosted us in their territory.  We also offered up a twelve, thirteen, twelve and ten percent share, respectively, of our take.  For you, if you'll allow me to make an opening offer, I'd suggest ten thousand dollars up front and a fourteen percent share of anything we gain.  We'll be saying for ten days.''



``So you'll give me fourteen percent when you offered less to others.  You think you're flattering me.''



``Yes.  We're staying a little bit longer here.  We looked into it, the heroes don't have a strong presence here in your Charlestown territory.  We can get away with just a little bit more.''



``Don't think I won't look into the amounts you just gave me.''  Accord was using a stylized fountain pen to make a note on a pad of paper.  Trickster wasn't entirely sure, but the paper didn't seem to have lines, and Accord was still making them meticulous, with neat, tight, flowing script.



``I wouldn't lie,'' Trickster said.  ``That's a good way to get killed, and I rather like being alive.''



``It has its moments,'' Accord said.  He wiped the end of the fountain pen and snapped the lid into place.  The pen joined all the other objects on the desk, arranged with explicit care to even spacing and hard right angles.  It was almost artistic, the way things were arranged for both size and utility, and the uniform nature of the aesthetics, with the colors and materials seeming to flow from object to object.  Silver and wood in dark cherry.



Accord looked down and corrected the position of the pen on his desk before turning back to Trickster.  ``Fifteen thousand dollars, and fifteen percent of any take.  The heroes don't have a strong presence here because they don't \emph{need} a strong presence here.  I maintain the peace.  It will cost me if I have people here, active and causing trouble.''



\emph{A little steep.}  ``I'll have to discuss that with my teammates.''



``Before you do, let me make you an alternate offer.  You do mercenary work?''



``We do.''



``I'd like to hire you for a task.''



``What task?''



``I'd like certain items stolen from a rival.  I can describe them to you and show you photographs.  Do this for me, and we'll waive the fee for entering my territory.  Also, I'll concede to have my share cut down to a mere ten percent.''



``Which rival?''



``Blasto.  A tinker.  Not quite the destructive personality his name implies.''



``I read up on him.  Blasto from the latin prefix, meaning bud, germination or seed.  Tinker botanist, grows walking, sentient plants in giant glass tubes.''



Accord gave Trickster an approving nod.  ``Yes.  Tinkers are\ldots bothersome.  Tinkers who work \emph{wet} are \emph{especially} bothersome.  They \emph{build, }they learn from past research and past projects, each thing is created more elegantly or \emph{faster} with the tools they've designed and amassed over time.  A tinker designs a better welding torch, to use an analogy, and that allows him or her to build a better power drill.  And so the cycle continues.  Steal Blasto's tools for my trophy case, it will set him back weeks or months.  I'll give you a further bonus if you destroy any other projects of his, as well as any computers or blueprints.''



``Dangerous, to attack a tinker in his lair.''



``Ah, you want more than just the waiving of your hospitality fee?''



Trickster was careful to be diplomatic.  ``No offense intended.  If Blasto was that easy to handle, I'm sure you would have dealt with him already.''



``Agreed.  Hm.  As you surely already know, I am a craftsman.  Not a tinker, but I use my power to create quality goods.''



``I'm aware.''



``I will pay you a moderate sum, and I will also supply a set of costumes for your team.  Use your free time over the coming week to make notes on what you desire.  Newspaper clippings, printed images or links to online images each of you individually like.  They do not necessarily need to be of costumes or clothing.  I would meet each of your teammates to assess their preferences.  With that, I can \emph{guarantee} you costumes that everyone in your group will like.''



\emph{And you bring the world a little more in order, }Trickster thought.  Accord was a thinker, and the running theory on his power was that he got naturally smarter as the problems he was addressing got more complex.  It gave him an intuitive understanding of groupthink, politics, and convoluted designs.  It also made him a local warlord capable of devastating counterattacks.  The power failed to grant him the same advantages in a one-on-one fight, and he wasn't quite the same battlefield strategist when it came to direct assaults.



Which was, Trickster understood, why Accord wanted him and the other Travelers to handle the attack on their own.



``Only four of us need costumes,'' Trickster said.  ``The other can make her own.''



``Only four costumes?  When there are seven of you?''  Accord's tone made it all too clear that he knew he was admitting knowledge he shouldn't have.



\emph{He knows about Noelle}.



``When there are seven of us, yes,'' Trickster said, feigning a lack of concern.



The door banged open.  Trickster tensed, his power reaching, even before he saw the threat.



It was Sundancer, with the receptionist following quickly behind.



\emph{Idiot}, Trickster thought.  \emph{I told you to stay back}.



``Trickster,'' she said.  Then she saw Accord.  ``I'm sorry for interrupting.''



``The deal was for a one-on-one meeting,'' Accord said.  His tone was strained, indignant.  Accord looked at his receptionist. ``You didn't warn her at the door?''



``I tried,'' the receptionist said.  ``She charged on through.''



``It's an emergency,'' Sundancer said.  ``Trickster, we--''



``Shut up,'' he said, and the tension in his voice coupled with Accord's seemed to clue Sundancer into the gravity of the situation.



She fell silent.  \emph{She's smarter than this, which means the situation's bad}.  \emph{But I can't do anything about it until I finish dealing with Accord}.



His heart was pounding.  ``Go wait outside, Sundancer.  I was in the middle of a meeting.  If Accord is willing, we'll wrap up this business quickly, I'll\ldots offer him something by way of apology, and then I'll come and talk to you about the issue.''



Sundancer backed towards the door, turned and left.



``Very sorry, sir,'' the receptionist murmured.  She closed the door.



Accord stepped over to the window behind his desk and stared outside.  Trickster waited patiently as the man composed himself.  Long seconds passed, and Trickster couldn't help but imagine the worst case scenarios that would have Sundancer forgetting common sense and crashing a private meeting between supervillains.



``I am something of an oxymoron, Trickster,'' Accord said, turning around.  He was measuring his words, stretching out the sentence, as though he were fully aware that Trickster was now in a hurry, and he wanted to apply pressure.



``Is that so?''



``You see, I deal with complicated things,'' Accord touched his mask, ``And I excel at them, but deep down, I'm a very simple person.''



``I think we're all very simple when you look past the surface,'' Trickster said.



``Quite so.  I like \emph{order}, Trickster.  Order means everything has its place,'' Accord touched his desk, moved his chair a fraction of an inch so it was squarely in place.  ``And every\emph{one} has their place.  Your subordinate's place was not \emph{here}.''



``I understand.  I'm willing to make amends.''



``Of course,'' Accord said.  He looked up and met Trickster's eyes.  ``I will be rescinding my earlier generosity.  Fifteen thousand dollars \emph{will} find a way into my hands within the next twenty-four hours.''



``Agreed,'' Trickster said.  \emph{There goes our pocket money}.



``You'll do my favor for me and expect no recompense.''



``Okay.''



Accord paused, seemed to consider something.  ``She'll have to die, of course.''



Trickster tensed.  \emph{Really, really didn't want to have to fight this guy.  }``Let's\ldots not be so hasty.''



``There are two kinds of people in this world, Trickster.  Some fit into the intricate machine that is society, and they serve as cogs, gears, levers and weights.  I think you're like that.  I liked you right off.  Even your power\ldots balance, isn't it?  Move things from one place to the next, but things remain fundamentally \emph{equivalent}.''



``Well said,'' Trickster replied.  His mind was racing.  How to convince the lunatic to leave Sundancer alone?  If he couldn't, would it be better to fight and kill Accord \emph{now }or wait until he could recruit the others?  Accord wouldn't have invited him to a meeting if he didn't have some kind of safeguards.  Traps?  For all Trickster knew, there was a pitfall in the floor or dart traps in the walls.  Accord's power, his knack for complexity, would make it trivial to weave such things into the architecture of his home and office.  If he knew, he could use his power, time it to put Accord in the way of his own trap\ldots but it could be something else entirely.



Accord was still talking.  ``Others aren't so accommodating.  They are freefalling, \emph{careening} elements, bouncing off any and every surface, damaging everything they touch.  Pyrokinetics so often fall into this category, I've found.  Rest assured, it's better to eliminate this disordered element before it does too much damage.''



Trickster couldn't find the words to reply.  \emph{Think, Krouse, think!}



``What a shame, such a young girl,'' Accord sounded genuinely upset.



``What if\ldots'' Trickster started, his mind racing.



``Yes?''



``What if I told you she was an agent of order in the universe?  That this situation, it's not \emph{her} that's causing the discord?  Like us, she's just reacting to another force?''



``You don't know the details any more than I do.''



``True.  But I know \emph{her}.''



``You're biased by virtue of being her teammate.  I see no other way than to act decisively.  Would you like to do the honors, or should I?''



``I'll show you what I mean.  \emph{She'll} show you.''



``Oh?''



``Just give me a second to go get her.  Maybe a bit of time to prepare--''



``Ten minutes, Trickster, and only because I like you.''



``Ten minutes,'' Trickster answered him.



``And she comes alone.  If she's truly an ordered individual, she'll show me for herself.''



Trickster nodded, turned and walked calmly out of the office, counting in his head.



The second the door was closed, he bolted, checking the time on his cell phone.  \emph{That'll be ten minutes exactly}.  He set a timer, subtracting the time it had taken him to leave the office.



The entrance that led to Accord's personal office was set in an alley, out of sight of the streets.  Trickster found Sundancer waiting.



``Trickster, it's--''



``Stop,'' he said, checking the phone.  \emph{Seven minutes left}.  ``Where's your phone?''



She pulled it from her belt, ``We--''



He used his power to swap her cell phone for his.  ``No, \emph{listen carefully}.  You just threw a neurotic, perfectionist supervillain's world into disarray by intruding on our meeting like that.  He's now rather intent on executing you for it.''



``What?''



``And he's a little guy with some \emph{big} muscle at his beck and call.  We could maybe deal with them in a pinch, but it wouldn't be pretty.  So I'm going to use your phone, call another member of our team to get filled in the emergency.  \emph{You're} going to fix your mistake, and you'll do it in\ldots six minutes and twenty-three seconds.  Look at the screen of my phone.  That's your deadline.  Go, stop by a bathroom, tidy your hair, get it wet and comb it if you have to, but look \emph{proper}.  Better to look \emph{neat} than to look pretty, understand?  When the timer hits zero, you'll walk into his office, then you'll perform a ballet routine.''



``Ballet?  Krouse, I haven't done it seriously in \emph{two years}.''



``Pick a routine you can do perfectly over one that's fancier or whatever.  Do it, apologize profusely for the intrusion, then bow out and leave.  If he gives any sign he's not satisfied, or the \emph{second} you fuck up, set the place on fire and scram.''



``Krouse--''



``Call me Trickster when I'm in costume,'' he corrected, his voice hard.  ``Don't worry about burning him alive.  He'll have escape routes.  You have five minutes and forty seconds, now.  It took me three to get from his office to here.  \emph{Go}.''



Sundancer rushed to get inside.



Trickster called Oliver.



``Marissa?'' Oliver asked.



``It's Trickster,'' he replied.  \emph{Need to talk about being more secure with our names.  ``}What's going on?\emph{``}



``It's Cody.  He touched Noelle.''



Trickster froze.  ``How bad is it?''



``\emph{Three times}, Krouse.''



``Three,'' Trickster said.  ``Fuck me.  I'm on my way.''



\sectionbreak



\emph{There's no way Cody's stupid enough to make contact with Noelle}.



\emph{There's no way anyone would do it three times.  How?}



Throwing caution to the wind, Trickster moved through the crowd of people by swapping with them, zig-zagging from one side of the street to the other, scanning the crowd.  People ran to get away from him as he appeared, but he didn't care.  Just needed to minimize the damage.



\emph{Minimize the damage.  It's becoming a running theme.}



He found his target not by spotting him, but by seeing the reaction from the crowd.  People were hurrying to get out of his way, running away.



The guy was naked, covered in gnarly, tumorous growths, and was moving at a limping run, attacking anyone he could get his hands on.  One of his arms was larger than the other, and a fluid-filled blister covered his entire stomach, sloshing with the contents.  His jaw didn't fit right, and had dislocated on one side, giving him a lopsided yawn.



A man shoved him and ran, sweeping his two children up in his arms as he fled.



Three seconds later, the man snapped back into the same position, in front of the creature.  Perdition\ldots Cody.  Except not quite.  The man carried through the shoving motion, but Perdition wasn't there any more.  Shoving empty space, the man stumbled and was clubbed over the neck and shoulders with a massive, misshapen fist.  He hit the ground with enough force that Trickster doubted he'd rise again.



The two children had fallen to the sidewalk when the man disappeared.  Perdition advanced on them.



Trickster crossed the street, swapping himself for one of the people who was fleeing the scene.  The children were running, but Perdition wasn't one to let his targets slip out of his grasp.  The six year old didn't get more than three steps before getting reset to his original position.



``Hey!''  Trickster called out.  ``I'm the one you want!''



Perdition spun around, and Trickster was already swapping himself for someone else, not allowing his opponent more than a glance.



\emph{Hide in the crowd}.  \emph{Can't allow him a chance to get me}.



``Kroushe!''  Perdition screamed.  He couldn't completely close his mouth, and slurred the words.



\emph{Inconvenient}.



``Keell you!  Mehk it shlow, mehk you beg an' crah and sheht yershelf lekk a baby!''



The little kid was getting away.  Trickster allowed himself a sigh of relief.



``Shheh wush mine!  An' you ruinn herr!''  Perdition screamed at a volume that distorted his voice even further, left it ragged.



Trickster winced.



``Muh cahreer, muh frenndsh, my guhll!  You `ook hem!  Yer a `\emph{hief!}``



Some of the time, the powers would be different.  Most of the time, going by precedent, they were \emph{stronger}.  Trickster was left to wonder how Perdition's powers had changed.  Duration?  Range?  The amount of time reversed?



Then his surroundings flickered, half the crowd disappearing.



Trickster didn't waste a second in swapping himself elsewhere, moving across the street.



Perdition was only just turning in the direction of where Trickster had been.



\emph{He doesn't need to see me now?}



Trickster saw everything shift again.



\emph{He's got a lock on me.  }\emph{Not as strong when he does it this way, but he can track me, force little jumps backward}.



Perdition charged, and the crowd scattered.



He reached for his belt, saw another shift, and Perdition was suddenly twenty feet closer, a few steps away.  With no time to follow through, Trickster swapped himself out of the way.



-And only belatedly recalled that he was putting another person in Perdition's path.  Perdition knocked a young woman to the ground, grabbed her, and then slammed her into a wall.



She wouldn't have survived the impact.



``Kroushe!'' Perdition roared.



Another shift hit.  \emph{They're about ten seconds apart, and he's hitting me for anywhere from one to five seconds each time}.



Perdition was halfway across the street.  With the way the crowd was scattering and the number of available people to swap with was dwindling, he was running out of options.  He could run or he could stay and fight, virtually powerless.



He stayed, reached to his side, and unbuckled the largest pouch on his belt.



Perdition was getting closer.  He seemed to have only a general sense of where Trickster was, wide, mad, bulging eyes roving over the crowd.



Trickster swapped himself for someone else, waited until Perdition started to turn, then did another swap.



Perdition paced from one side of the street to the sidewalk, between the last two of Trickster's chosen destinations.



Only one or two seconds were left before the next automatic time skip.



Trickster swapped himself for the body of the girl who Perdition had thrown into the wall, drew his gun and fired it, all in one smooth motion.  Screams of alarm erupted in the wake of the gunshot.



He stepped closer, then emptied the remainder of the clip into Perdition's head and chest.



He swapped himself for someone in the lingering crowd, grabbed the closest person.  ``I hope you own a car.  Because you're going to lend it to me.  Fast.''



\sectionbreak



Krouse pulled the car into the driveway.  Oliver was outside, and hurried to Krouse's side.



Oliver was taller than him, now.  The baby fat was gone, and he was \emph{fit}.  Krouse had wondered at times why Chris had been so attractive to the ladies.  He didn't wonder with Oliver.  Oliver was attractive in a way that meant he could model, he was naturally athletic, he was even smart.  It was scary how fast he was picking up new skills.



But he was still \emph{Oliver.  }Whatever gradual transition his power was offering, it hadn't changed the person at the core of it; an insecure, socially stunted teenage boy.  In a way, it had made it worse.  Oliver's face and body changed according to his basic perception of attractiveness, and that changed a little every time he saw a new face.  In little ways, his face changed day by day, to the point that it wasn't always easy to recognize him.



\emph{Fuck you, Simurgh}, Krouse thought.  They'd all been forced to deal with their individual tragedies.  Noelle's went without saying.  Jess hadn't gotten to walk, Luke hadn't gotten to fly, Oliver got a physical and mental overhaul without any fixes for the \emph{real} problems, and Marissa had been thrust into the situation she'd fought so hard to escape, where she was forced to pursue a life she didn't want.



Krouse's tragedy was waiting for him inside.



As for Cody's\ldots



Oliver helped Krouse move the body out of the passenger seat.



They grunted as they carried it through the front door.  Krouse double checked nobody was observing.  He'd parked briefly to remove his costume, then swapped himself and the body for people in another car before continuing en route to their current hideout.  It was the middle of the day, and virtually everyone in this neighborhood would be at work or at school, but he feared some college student or elderly person would just \emph{happen} to be outdoors or walking a dog.  It would make things complicated.



Accord wasn't so wrong on that subject.  Things were better when they were simple.



Krouse and Oliver dragged the body to the middle of the living room.  It joined two others.  Each was different in the mutations, in the distortions and impurities.  Each of the three bodies was Perdition. \emph{Was}\emph{Cody}.



He looked at Ballistic, Jess and Oliver.  ``Three?  You're sure?''



``Sure enough,'' Ballistic said.



``How's she?''



``Upset.  You're going to have to talk to her, calm her down.''



Krouse winced, nodded.



They all stared at the bodies.  This would be the third incident.  Or incidents three through five, if he wanted to count it that way.



``How much damage done?'' Krouse asked.  ``Anyone hurt?''



``A bunch hurt but nobody got killed by the one I went after,'' Jess said.



``Yeah, a few hurt,'' Ballistic said.  He paused.  ``One dead.''



``Fuck,'' Krouse said.  ``At least two dead at the hands of the one I stopped.  Not as bad as last fall.''



Ballistic shook his head.



``We\ldots we can't let this happen again,'' Jess said.



``That's what we said last time,'' Krouse noted.



``She's getting stronger,'' Jess said.  ``And more volatile.''



``We'll fix her,'' Krouse said, his voice a touch hollow.  ``We'll fix her, and we'll get home.''



\emph{Just words.  How can they believe me when I don't even buy it?}



``Where is he?'' he asked, breaking the lingering silence.



Ballistic pointed in the direction of one of the ground floor bedrooms.



``What happened?'' Krouse asked.



``We don't know.  Neither Cody or Noelle are saying.''



``\emph{Fuck}.  Okay.  I need a smoke, then we'll resolve this.''



``Krouse--'' Luke said.  But Krouse was already out of the living room, pushing his way through the front door.



He stepped outside, sat on the front steps, took his time in getting his cigarette and lighting it.  He finished the first, started on the second, and gave serious consideration to having a third after that.



He shut his eyes.  \emph{Just need a moment of calm, a few minutes to organize my thoughts}.



``Krouse.''



He resisted the urge to sigh.  Marissa was there, coming down the path from the driveway.  ``Mars.  Glad you did okay with Accord.  Sorry to leave you like that.''



``It's okay.  It was better that you went to deal with the situation.  I couldn't have.  I don't have it in me, even knowing they aren't \emph{real}.''



Krouse nodded, closed his eyes.



``He said I wasn't perfect.''



Krouse froze, turned to see her leaning against the railing just beside him.  She'd changed into civilian clothes.  ``You burned his place down, then?''



``No,'' she said.  ``He said I wasn't perfect, but that he saw what you meant.  He said I was trying, despite myself.  I\ldots I don't know if that was a compliment or not.''



``Ah.''



``Um.  He wants you to see him tonight.  Nine sharp.  And, um.  He said that if I'm not the problem, he fully expects you to bring the \emph{real} culprit.  Did he mean Noelle?''



``Cody,'' Krouse said.  ``Shit.  Not the way I wanted this to go.''



``What!?  Krouse, he's going to kill him.''



``Probably.''



``We can't!''



``We may have to.  If we don't give him a scapegoat, he'll send assassins and homicidal underlings after us.  We need \emph{someone} to blame, not just for intruding on the meeting, but for the three very violent scenes that erupted in his territory earlier today.  Not to mention that we can't afford to pack up shop and move right now, not while Noelle's as upset as she is.  Between the two of us, I think we've charmed Accord enough that I'd bet we can get away with giving him Cody and paying him a fair sum.  We do that, we can stay for ten days.  We'll gather some funds and give Noelle time to quiet down.''



``You're talking about killing a teammate.''



``He was \emph{never} a teammate.  He was one of us, yes, but he never cooperated, never worked with the rest of us.''



``We made a pact, a \emph{promise.  }To stick together, no matter what.  To do what it took to fix Noelle and get home.''



Krouse shut his eyes.  ``I \emph{know}.  Not an hour goes by that I don't think about it.''



``You're breaking that promise if you give Cody up.''



Krouse sighed, took a drag of his cigarette and blew smoke out through his nostrils.



``Krouse-``



``Mars.  There's no reason he'd enter her room and intentionally touch her three times.  You know that, I know that.''



He turned around to glance at her, saw her frowning.



``What do you mean, Krouse?''



``I mean he waited until the rest of us were busy, then he entered her room and he enraged her.  Because for there to be three points of contact, three uses of her power, \emph{she'd} have to be the one making the contact.  \emph{She'd} be using her power on purpose, and she wouldn't do that if she wasn't berserk.  I'm guessing he was badly hurt?''



``Broken arm, broken leg.''



Krouse nodded.  He took another drag of his cigarette.



``Why?  How?''



``He had a goal in mind, only he didn't anticipate how fast she moves, how strong she is.  He was trying to do one of two things.  Either he did something general, said something, with the aim of making her go berserk\ldots or he tried to kill her.  One way or another, Cody wanted to end this.  End our mission.  Free himself.  He doesn't give a fuck about the promise, so I don't see why the promise should protect him.''



``I don't- I can't believe that.''



``You can't believe that \emph{Cody} is that self-centered?  Did you just come from an alternate universe with a different Cody?''



``No.  I\ldots I can almost believe it.  But you're talking about \emph{killing}.  Or giving him to someone else so \emph{they'll} kill him.''



Krouse finished the cigarette and tossed it to the base of the steps, crushed it under his toe.



``Tell you what,'' he said.  ``Let me talk to the others.  Maybe Cody too, just to confirm suspicions.  We'll see if the others come to the same conclusion.''



``Krouse, you're talking about sentencing Cody to death.''



``He knew what he was getting into.  And whatever else happened, three innocent people are dead because he fucked up.  So we'll talk to the others.  We'll come to a consensus.''



``This is ugly.  \emph{God}, Krouse, it's still \emph{Cody}.''



``Yeah.  It's not pretty.  So why don't you take a break, clear your mind?  Maybe go do a food run for Noelle.''



Marissa frowned.  ``Hate these runs.''



``We have to, and your turn's up.''



``I know, I know.  But people look at me funny when I bring a cart of meat and only meat.''



``Tell them you're buying for a restaurant and the wholesaler dropped the ball today.''



``It still looks \emph{weird}.''



``Maybe find a butcher?  We've got a backyard here, if you want to get maybe two whole pigs, you can tell him you're throwing a party.''



``Fuck it,'' she muttered.  ``Keys?''



Krouse fished the keys and the carton of cigarettes from his pocket.  He tossed her the keys and tapped another cigarette out of the box.



``And stop smoking.  You're killing yourself, Krouse.''



``I know,'' he said.



She was all the way at the car when she turned around and hurried back to the front steps.



``What?''  Krouse asked.



``I almost forgot.  Accord.  He wanted me to pass this on.''



She handed him a piece of paper.  There was a number printed on it.  Different area code.



``What is it?''



``He said someone was trying to get in contact with you.''



``Who?''



Marissa shrugged.



``For the record, Marissa, with guys like Accord, you can't \emph{almost}\emph{forget} to pass on messages, and you don't waltz in on a business meeting.  Things could have turned out a lot different today.  They still might.''



``I\ldots I don't \emph{want} to interact with guys like him.''



``We have to.  Only way to go about it.''



``I know.  I just\ldots next time we run into someone like that, I'll stay hands off.  Keep my distance.''



``Alright.  Go, shop.  Take your time.  Give yourself a break, buy an ice cream or something.  You have my permission and my \emph{orders} to go distract yourself.''



Marissa retreated to the car.



Krouse puffed for a minute on his second cigarette, pulled out his phone, and dialed the number.



``\emph{Hello?}``



``Accord gave me this number.''



``\emph{Then this would be Trickster, I presume.}``



``Yeah.''



``\emph{I have a business proposition for the Travelers.}``



``Well, things have gone a little south with Accord, here, so I'm not quite sure where we stand, but I need to do this job for him before I take on anything else.''



``\emph{This is more of a long-term job.}``



``We don't really do long-term.  We don't stay in one place for long.''



``\emph{I'm well aware of your circumstances.}``



Trickster took a long haul on his cigarette.  ``That so?''



``\emph{I know Accord through a mutual acquaintance.  Through this acquaintance and my own resources, I've gathered a fairly robust set of data on you Travelers.}``



``That sounds vaguely threatening.''



``\emph{I suppose it might, to individuals trying to avoid scrutiny.  Rest assured, it is just the opposite.  I know what issues you face, Trickster, and I am offering you a solution.}``



``A solution?''



``\emph{I'm offering three things, to be precise.  Work for me.  Help me achieve my goals and I will allow you to achieve yours}.''



Krouse leaned forward, putting his elbows on his knees.  he held the cigarette in one hand and the phone in the other.  ``What do you know of our issues?''



``\emph{I know what the PRT knows.  I know you appeared out of nowhere, that a Luke Casseus and a Noelle Meinhardt were admitted for care to St. Mary's hospital, yet there are no such students on any high school rosters.}``



``We're not from there,'' Krouse said.



``\emph{Then why did Luke Casseus put down Madison, Wisconsin as a place of residence?}``



Krouse suppressed a groan.



``\emph{Rest assured, Trickster, there is no need for any alarm.  The fact that I know these things is an asset to you.  A contact of mine in the PRT has taken over your case file and requisitioned all details on your encounter with Myrddin.  That case will not be pursued further.}``



``And why are you doing this for us?''



``\emph{Because I have goals of my own, and I believe one can't be too careful.  When hiring expert help, I prefer that help to be loyal.  I will get that loyalty by giving you what you desire.  Everyone has their price, and my research into you Travelers has been done with the goal of discovering what that price is.}``



``Yeah?  Let's hear it.  What's our price?''



``\emph{All the money you require, for one.  So long as you're in my employment, I will pay for whatever you require.  Even if it is nearly one thousand, five hundred dollars in groceries per week.}``



``How generous.''



``\emph{Number two?  I will send you home.}``



Krouse stopped, the cigarette dangling from his lips.



``\emph{A man in power like myself has contacts.  Through one of these contacts, I have access to a man who can create doorways between worlds.  The caveat is that I won't have the power, funds or leverage to request assistance from this individual until my own goals are met.}``



``So we have to help you for you to help us.''



``\emph{Exactly, Trickster.  As for your other problem, well, that is a more daunting task.}``



Noelle.



``You said you could help.''



``\emph{I can't guarantee anything.  I can offer all of my resources, which are considerable, and all of the resources I will have, which are even more so.}``



``Sounds pretty wishy-washy.''



``\emph{Perhaps.  But when making an argument or making a sale, I find it's best to lead with the second best offer, move on to the weaker ones, and then close with the best.  I am offering you one more thing.}``



``What?''



The man on the phone told him.



It was another minute before Krouse hung up.



Krouse spent fifteen more minutes sitting on the front steps of the house.  It was the first time in a year that he'd had a moment to stop and think and he didn't reach for his  cigarettes.



When he stood, he was in something of a daze.



He stepped back inside.



``Krouse,'' Luke said, ``We need to talk about what we're doing with Cody.''



``Later,'' Krouse said.



``What's going on?''



``Going to go talk to Noelle.''



``She's pissed, Krouse.  She'll flip out on you, and I'm \emph{not} doing this again.  I \emph{won't} fucking hunt down deranged mutant clones.  \emph{Especially} not yours.''



``Not an issue.  She'll like what I have to say.''



``Krouse-``



``\emph{After}, Luke,'' Krouse said.  He spun around, faced his friend. ``I think we've got what we're looking for.''



``What?''



``A way home.  Maybe even a fix for Noelle.''



``How?  Who?''



``Some supervillain in Brockton Bay.  Wants us to work for him for a little while.  There's more, but\ldots''



``But?''



Trickster met Luke's eyes, ``I want to tell her first.  Everything that's happened, I have to.''



``We deserve to know too, Krouse.  We've been working at this as long as you have.  We've had our hopes up and had them dashed too.  Too many times.''



``I know.  I know.  Just\ldots I'll tell you after I've told her.  I think this is it.''



He caught a glimpse of Luke's expression as he turned away.  A look of deep sadness.  Krouse hesitated.



What was he supposed to say?



``Just a few minutes,'' Krouse said, ``I'll be back, then I'll explain.''



He made his way to Noelle's room, knocked.



``\emph{Go away}.''



``It's Krouse.''



There was a long delay.



``What do you want?''



``I want to come in,'' he said.



``No you don't.''



``I do.  Please.''



There was a long delay.  He took that for assent.



Noelle didn't meet his eyes as he entered.  He noted the mangled bedframe, the splintered wood from the boxspring, and the mattress torn in two.  An oak cabinet had been demolished, and both bedside tables were in ruins.  There wasn't a single intact piece of furniture left.



He turned towards her.  ``I-``



``Don't look at me,'' she said.



He stopped, then he seated himself on the floor with his back to the remains of the cabinet, his back to her.



``Come to talk?'' she asked.  ``Keep me company?''



``I was planning on doing it a little later. Things are kind of a mess out there, you know.  The Cody situation.''



``Nobody keeps me company any more.  Only you.''



``Yeah.  But that's not why I'm here.''



``You want to know what happened with Cody.''



``I \emph{know} what happened with Cody.  He tried to kill you.''



There was a long silence.



``I can't die, Krouse.  I've tried.  Tried to end it.  Spare you guys from looking after me.  I can't.  Nothing works.''



``Yeah.''



``I'm one of \emph{them}.  Or I'm becoming that way.''



``Maybe.''



``An Endbringer.''



He felt a chill, and it wasn't the early spring temperature.



``Maybe.  Or maybe you're more like those monsters that were dumped on the street.''



``\emph{They} could die.  You told me that you killed one of them.''



``Probably.  But I saw another one die, you're right.''



``And my power, if I get stronger, if I get more out of control-``



``You won't.''



``I'll be just as bad as the Simurgh.  In a different way.  I touch someone, and then I spit out copies.  Uglier, stronger\ldots meaner.  I can't control them.  If I got my hands on one of the major heroes?  Someone like that Myrddin guy?''



``You \emph{won't}.  Listen to me, Noelle.  I was just talking to someone.  We may have an answer.''



He heard her shift position, flinched despite himself.



``You've said that before,'' she said.



``This sounds like \emph{it}.  He's not saying he \emph{might} be able to make something that can get us home.  He's saying he already knows someone who has a way.  Someone who goes back and forth.  And he knows people.  Scholars, scientists, this one girl with powers he didn't explain, who \emph{knows} stuff.  Like Accord does.''



``The guy you saw today?''



``Yeah, the one I told you about,'' Krouse was getting excited, despite himself.  ``The way this guy described it, there's a solution out there, and he can get it.''



``Krouse, it's- it's not that easy.''



``I know.  I know it's not easy, but there was a third offer on the table.  A third thing he was giving us.  He said we should consider it a bonus.''



``What?''



``\emph{Hope}, Noelle.''



``I don't understand.''



``He just got someone working for him, and this person can see the future.  And she says there \emph{is} a way to help you.  Definitely.  Chances are low, but he says he's confident he can maximize them.''



``He could be lying.''



``No, listen.  The Simurgh?  This guy said she has a weakness.  Two ways where she \emph{can't} see the future.  Two ways to break free of her cause and effect.''



Noelle didn't say anything.



``The first way, you've got to be basically immune to powers.  \emph{Scion} is.  He's immune to precognition, throws everything out the window when he shows up.  I saw it when he fought the Simurgh.  She couldn't automatically dodge his stuff, because she either couldn't read his mind or she couldn't see the attacks before they happened.  So he hit her, a bunch of times.  I saw it.''



There still wasn't a response.



Krouse was getting more excited, had to press his hand flat against the floor to stop it from shaking.  ``And the other way?  There's thinker powers that mess with her ability to influence events. If another precog gets a hand in events, the Simurgh automatically shuts them down and vice-versa.  The way this guy said it, the precogs get overloaded with the second-guessing the other precog, on top of having to figure out all the quantum possibilities and split paths.  And this guy?  He has a power that messes with precogs some, and the \emph{precog working for him} has a power that will help circumvent the Simurgh's power.  Get it?  So long as we work for him, we're free of it.  No more cause and effect.  No more feeling like we're doomed no matter what choice we make.  We go from that kind of safety to \emph{home.  To our world.}``



Krouse turned around, and despite himself, he was smiling.  He had to blink rapidly to clear the tears that were collecting in his eyes, threatening to run down his face.



Noelle was perched on the ruined bed.  Her fingers were clutching a sweatshirt, with no shirt beneath.  Still the Noelle he'd always known.



From the waist up.



Around where her pelvis should have been, she'd changed.  The mass of tissue left her tall enough that she had to hunch over to avoid hitting her head on the ceiling, and she was lying down.  Half of it was angry, red, wrinkled or blistered.  The other half was smooth tissue, dark greens, dark brown and pale grays.  The head of an animal, half-bovine and half-canine, extended from the front, large as a horse from the back of its skull to the tip of its flaring nostrils.  Another head was in progress, emerging just to the left.  Two forelegs extended to either side of the heads, rippling with powerful muscle, ending in something that fell between claw and hoof, massive and easily capable of tearing through steel.



There were the fingers and thumb of a hand, extending from her right hindquarters, each digit thicker around than Krouse was, with another, smaller limb extending from the palm.  Her rear left hindquarters featured only a mess of tentacles, some bearing partial exoskeleton, some long enough that they had to encircle the massive head and numerous limbs, or wind in a wreath around her as she lay down, lest their coiled mass fill the master bedroom of the house and leave Krouse nowhere to sit.  Despite the apparent lack of bones, the tentacles \emph{were }capable of supporting her weight.



She didn't expel waste.  She only grew, or she reinforced what had already grown.



She'd tried to starve herself, to die of thirst.  It had turned out badly.  She'd gone berserk and killed forty people in one autumn night.  Their tissues had played a large part in building the massive fingers and thumb that extended behind her.



The others didn't know \emph{quite} how bad things had gone, then.  He'd managed to shield them from the news reports, the total body count, had kept them moving from city to city until the story died away.  They knew people had died, they didn't know it was \emph{forty}.



It was bad.  A bad situation overall, one that had Krouse retreating from the house in the dead of night, just to find the most remote location he could reach, to weep, to scream his frustration, rage, shame and guilt and not worry about the others hearing it.



But with all of that, with her sheer intimidating \emph{presence}, he was nonetheless able to look up and meet Noelle's eyes.  Hers were welling with tears, too.



``I believed what he was saying,'' Krouse said.  ``I think this might be it.  Our best chance.''



``You think so?  We can hope?''



``We can \emph{hope,}'' he repeated, whispering the words, as much to himself as to her.



\sectionbreak



A wave crashed against the beach.



He hurt all over.  His body wasn't listening as he told it to move.  His hand slipped on the pavement as he tried to push himself up off the ground.  There was sand filling the cracks in the pavement, denying him traction.



He flipped himself over onto his back, instead, then sat up.  He wobbled as he stood.



The first thing he saw was Jess.  Jess in her wheelchair, at the edge of the grass, where it dropped down to the beach.  She was staring at the ocean.



``J--'' he started to shout, had to force more air into his lungs before he could.



``Jess!'' he hollered.



She didn't move.



Sundancer was lying beside him.  He raised her mask and checked that she was breathing.  She was just unconscious.



His eyes roved over the empty lot.  No people.  No soldiers.  No other parahumans.



His eyes settled on a dense cluster of seagulls.



Krouse nearly fell as he made his way towards them.  He didn't miss the tracks Jess's wheelchair had made.  She'd been here.  She'd seen.



The seagulls scattered as he approached.  He saw a white feather that had been left behind, ground it under his toe as he might one of his cigarettes.



The birds had been gathering around a mark.  A stain.  There wasn't a better word to sum it up.



It was blood.  Enough blood that whoever it had belonged to wasn't alive anymore.  Drag marks extended off towards one side of the lot.  The soldiers had taken the body, and the seagulls had taken much of the remaining gore.  All that was left were bits of skull, and little fatty blobs that might have been brain.  The bullet would have passed through and shattered the cranium, by the looks of it.



He had no doubt as to who had died here.  Could remember the scene as it had been just before he'd been knocked unconscious, could remember where people had been standing.



Another wave crashed against the beach.  He heard the seagulls cawing angrily, wanting the morsels that littered the ground in front of him.



Krouse spent a very long time staring at the stain.





