





I didn't trigger.



Kind of silly, really, that I'd expected to \emph{see} something.  But this was the opposite.  A trigger event worked on the power end of things.  This was altering \emph{me}.



I felt the range of my power halve, as though a guillotine blade had dropped down, cutting it off.



My control began to slip.  It wasn't so severe as the effect on my range, but I could feel it degrading.  I was aware of my bugs in a general sense, and they were moving in reaction to my subconscious thoughts, but the end result wasn't precise.  I moved them, but getting them to stop had a fraction of a second's delay.



Slipping out of my control.  Slipping\ldots



Tattletale was nearby, but I was trying not to focus on her.  I had to focus on the swarm, I needed to be \emph{perfectly} aware of what was going on.



An echo of an event from years ago, only this time, Tattletale was one of the ones in the dark.  I felt a pang of guilt,and I was surprised at how intense it was.  Guilt, shame, a kind of intense loneliness\ldots



\emph{This way lies madness}, I thought.  But the thought itself had an oddly disconnected quality to it.  The emotions persisted, and I was aware of the memories.  Walking away from the people I cared about, feeling horrible about it, knowing it was the best thing in the end.



Too many would be calling it an error in judgement, stupidity.  Why go to such an extreme, especially when there was no guarantee it was the right path in the end?



But it had allowed me to reunite with my father, in a fashion.



I could remember jail too, the way the guilt and shame had manifested as a maddening restlessness, worse than the confinement.  The fears that had haunted me, dealing with the other prisoners, the kind of peace that had come with surrendering to my then-current circumstances\ldots



Would this decision lead to something in the same vein?  Would I be confined, following a monumental decision that was so selfish and selfless at the same time?



I was altering something biological and mental.  I felt my heart skip a beat as my mind momentarily touched on what that kind of confinement might entail.



I was hyperaware of my own body, every movement, the flow of blood in my veins.  I was focused on the beating of my heart and my breathing, both picking up speed with every moment.



The sky behind me was bright blue, almost taunting me.  \emph{Blue was the color I wore when I became a hero.  A failure}.  It made for long shadows, extending down the length of the cave in the direction of the others, in the direction of Doormaker's portal to Earth Gimel.



\emph{No, focus on the swarm.}



My range was dwindling with every passing second, and so was my control.



That trace of fear I'd experienced swelled as I realized just how much I wanted that control.  I needed to be able to use my mind, to put things into motion when I had an idea.



\emph{I need control}, I thought.



I tried to open my mouth to tell Panacea, and I couldn't.  I'd pushed my focus out towards my swarm, and I couldn't reel it back in to my body.



I was still aware of my body, but it felt piecemeal, now.  My fist was shaking, I had my head bowed, my teeth clenched so hard against one another it hurt.  My heart was pounding, my breath coming out in inconsistent huffs through my nose, pushing just a bit of mucus free.  My eyes were wet with tears, but I hadn't blinked, causing them to build up on the surface of my eyeballs.



All of these things were normal, but I didn't feel like they were all intuitive parts of a whole.  My concept of my body as a connected thing had shattered, the ties broken.



If this continued, I'd be on autopilot from here on out, if I could even put the individual components together to walk.



\emph{I need control}, I thought.



A moment passed, and I could feel Panacea working to give me that control, changing what she was focusing on.  I felt the swarm moving more in sync with what I was thinking and wanting.  But this\ldots I could sense what was happening, feel my range plummeting yet again, the guillotine coming down.  My range had been cut down further.



Give an inch in one department, lose \emph{several} inches in another.  Lose a whole foot.



Everything was piecemeal now, slipping away.



If this continued, I'd have nothing left.  A net loss operation.



\emph{Stop}, Panacea, I thought.  \emph{Stop, stop, stop, stop\ldots}



My swarm attacked her, and it wasn't because of any conscious command on my part.  The attack was crude, more the swarming behavior of wasps drunk on attack pheromones than the calculated attack I was used to employing.



She stopped, pulling back and falling backwards in a clumsy way.



``Shit, shit, shit, fuck,'' a young woman's voice, from a distance away.  Not Panacea.



Tattletale.



I raised my head, and Tattletale startled a little.  Why had she startled?  The way I'd moved?



``What did you \emph{do}, Taylor?''  Tattletale asked.



\emph{What did I do}?  I wanted the answer to that question, myself.



I looked at Amy, realizing the bugs were still approaching her.  I pulled the swarm away, and I felt how hard it was to move them.



I was left with the ruins of my power.  My range was maybe a third of what it might otherwise be, the control rough-edged at best.  There were bugs in my swarm that I couldn't control, too small.



There were too many things to concentrate on.  The swarm, the nuances of my power, my state of near-panic, and the fact that I no longer felt like a complete, connected human being.  The other stuff, it wasn't that it wasn't important, but it was so \emph{secondary}.



Someone large, with flames swirling around his hands, stalking towards me\ldots didn't matter.  My power – was my inability to get a complete picture due to a loss of my multitasking ability?



It was Lung who was approaching, Lung who stopped a short distance away, his breathing hot, muscles tensed, flames rolling over his clawed hands and forearms.



He stared at me, his eyes a molten orange-red behind his mask, his breath hot enough it shimmered in the air.  Waiting to see if I was a danger?



``Taylor\ldots'' Tattletale said, as if from very far away.



But she didn't say anything else.  She stared for long seconds, and then she paced, walking around the edge of the room, as if she could get different perspectives on me from the edges of the room.  Bonesaw, a little distance away, was half-crouched, tensed, between me, Doormaker and the clairvoyant.  She looked less like a child and more like a wild animal.  Reverting to habit, maybe, only without the veneer of the innocent, cutesy, perky child this time.



The stillness of it all was eerie, not helping the growing sense of panic I was experiencing.  Everyone's eyes were on me, and I felt like I might be having a panic attack.  I couldn't regulate my breathing because focusing on that meant my body was getting tenser, my one fist clenched so hard it hurt.  Paying attention to my hand meant my breathing started to spiral out of control again.  All the while, my heart was pounding.  Nothing I could do to fix that.



I closed my eyes, in an effort to shut out the external stimuli, and I felt the moisture running down to the point where my lenses met my cheekbones, settling there.  I raised my head to look at the cave roof.



As if that was some kind of cue, Bonesaw dashed through the doorway.



Why was I crying?  It didn't fit.  I was scared, my hand was shaking and I couldn't be sure how much was fear and how much was because of what Panacea had done\emph{.  }I was \emph{angry}, inexplicably, frustrated, and I couldn't shake the phantom memories of being in jail.



Trapped in an uncooperative body?  No.  The emotions and the thoughts didn't match with that.  Why was I thinking about it, all of a sudden?



I felt almost nauseous, now, on top of the sense of panic and the conflicting, nonsensical emotions I was experiencing.  Or because of them, maybe.  I felt myself tip over as if I were \emph{physically} reeling from it all.  When my leg moved to catch me, it wasn't because I gave it the order.  It wasn't a reflexive response either.  A third party.



\emph{Passenger}, I thought.  \emph{I guess we're going to have to learn to work together here.}



My breathing eased a notch.  I had no way of telling if it was the passenger reacting or if it was my own reaction to the realization that the passenger was there.



``Weaver?''  A girl's voice.



I wasn't sure I trusted my control over my bugs to get a good sense of where she was or what she was doing.  I turned my head to see Canary standing by the portal.



``Don't,'' Tattletale said.  ``Don't bother her.  Leave her alone for long enough that she can get her bearings.  Wait.''



``What happened, Weaver?''  Canary asked, ignoring Tattletale.



\emph{Someone answer that question for me}, I thought.



\emph{Tattletale?  }No, she was silent.



Bonesaw was gone.



Canary wouldn't know.



\emph{Passenger?}  I thought.  \emph{Any clues?}



It was easier to talk to my passenger than it was to speak up and answer the question.  Speaking up meant voicing everything that was wrong, my confusion, the fears, the worries, the fact that my body, my mind and my emotions all felt entirely \emph{unhinged}.  Speaking meant trying to talk around the growing lump in my throat.



``You never learned to ask for help when you needed it,'' Tattletale said.  Her voice was almost accusatory.  ``I mean, you \emph{ask} when you approach other groups, and it's like you're holding a gun to their heads as you ask, or you ask at a time when it's hard for them to say no, because all hell's about to break loose.''



I glanced down at Panacea.  She wasn't moving, aside from rocking a bit back and forth as she breathed, her head slumped, eyes on the ground.



Was it \emph{me}?  Something grotesque?  Horrible?  Had I changed?



No.  I had taken stock of myself, I'd \emph{seen} myself, and I was still the same, as far as I could tell.  Two arms, two legs, two eyes, a working nose, ears and mouth.  One missing hand, but that was to be expected.



``Yeah, you asked Panacea.  You asked me to play along and arrange stuff, when you went to go turn yourself in.  Your handling of the school thing\ldots well, I don't want to get into a pattern and start cutting too deep.  Let's just say you make a decision by yourself, and then you use others to get help carrying it out.  That's not really you asking for help, is it?''



I didn't need this, not now.  But I looked up, meeting Tattletale's eyes.  She was standing behind Lung, now.  He was changing.  Was he biding his time?



``While I'm saying all this, kiddo, you gotta know I love you.  I adore you, warts and all.  You saved me, as much as I like to think I saved you.  All this stuff I'm bitching about, it's the same stuff that got us through some pretty hairy shit, and I love you for it as much as I groan about it.  You're brilliant and you're reckless and you care too much about people in general when I really wish you'd leave things well enough alone and be selfish.  But this?''



\emph{This?}



\emph{``Shit,'' }Tattletale said.  ``You gotta forgive me, just this once.  Because seeing this and knowing what you pulled hurts enough that I \emph{gotta} say this.  \emph{This} makes me feel really sorry for your dad, because I'm starting to get a sense of what you put him through.''



She might as well have slapped me full-force.  Worse, I deserved it.



\emph{So this is what it's like to be on the opposite end of a Tattletale attack}.



``There,'' she said.  She smiled a little, but it wasn't a \emph{grin}, exactly.  If it was an attempt at being reassuring, it wasn't something she had a \emph{lot} of practice in.  ``I've said what I needed to say.  I \emph{do} have your back, here.  Now we need to figure out how we're going to fix this.''



Which I was okay with, except I wasn't sure what \emph{this} was.



``\emph{This} isn't easily reversed,'' Bonesaw said.



She had returned, and she'd brought others.



Marquis, and two of Marquis' lieutenants.  They'd been delivering wounded up until a bit ago, but their hands were empty now.  Marquis was a little dusty, but still elegant and elaborately dressed without being feminine, his hair tied back into a ponytail.  He was accompanied by the hyper-neat guy and the guy with arms black from fingertip to elbow.  All three looked like they were in full on \emph{business} mode.



``I'm open to \emph{trying},'' Tattletale said.



Marquis surveyed the situation with a cool gaze.



``I'm not hearing a resounding \emph{yes} here,'' Tattletale said.



Marquis strode forwards.



``Careful!'' Tattletale called out.



I might have dodged if I'd had full control over my own body.  I might have dodged if I'd been a little more focused.  Hell, I probably would've dodged if it wasn't for the realization that Tattletale was warning \emph{Marquis} instead of warning me.



\emph{I thought she had my back}, I thought, as Marquis' shaft of bone caught me dead center in the chest.  I couldn't have dodged if I'd had full control over my body and my flight suit.  It hit me in the sternum, broad and flat, and shoved me back and away.



The bone \emph{changed }as it pushed me, splaying out in two branches.  The backwards momentum made it impossible to get my feet under me, which meant I hit the ground, rump first, then a heavy hit with the hard shell of the flight pack, and finally a crack of my skull against the hard stone floor of the cave.



I came to a stop, and was just beginning to get my bearings when Marquis continued extending the pole.  I was shoved further back until my back was against a stone, five feet from the cave mouth, five and a \emph{half} feet away from the sheer rock ledge above a sheer drop I couldn't measure with my bugs.  The two branches of bone sat on either side of my neck, like the arms of a dowsing rod, pinning me in place.



The skin of his other hand had ripped and torn as the bones of a massive skeletal hand had erupted from his wrist.  Judging by its position around Lung and Panacea, he'd apparently used the hand to push or slide them back away from me.



``Oh god,'' Panacea was saying, ``Oh shit, oh god.''



A sudden display of emotion, as confusing to me as everything else here.



And here they were, Marquis, his men, Lung, Panacea, Canary, Tattletale and the portal duo from Cauldron, staring me down.



``Sixteen feet,'' Tattletale said, her voice quiet.  ``Fifteen point nine-eight feet, to be exact, but we can ballpark it.''



Marquis nodded.  ``Parahuman abilities wax and wane depending on one's mental state.  Given how volatile she may be\ldots''



``It's not going to change,'' Panacea said, not making eye contact with anyone.  She was staring at the backs of her hands, which were flat against the cave floor, or staring at the tattoos that covered them.  ``I felt how it changed\ldots  Not connected to her emotions or those parts of her brain.  Not anymore.''



``I see.  Good to know, thank you,'' Marquis said.  He approached three paces, and the bone shaft that extended between his arm and the branches that pinned my neck shrunk a corresponding amount.



He was keeping a distance, a good twenty or twenty five feet away from me.



\emph{Why did Tattletale say sixteen feet?}



``What are you guys talking about?'' Canary asked.



``I would have burned her,'' Lung growled the words, ignoring her.  ``But I thought you would be upset if I burned Amelia in the process.''



``Quite right,'' Marquis said.  He didn't take his eyes off me.



``Oh god,'' Panacea was saying, her hands moving to her head, her fingers in her hair, inadvertently pulling it from the ponytail.  ``Oh fuck me, oh god.''



``Hush,'' Marquis said.  He laid a hand on her shoulder.



``Well, this is a step forward for you, Ames,'' Tattletale commented.



``\emph{Don't},'' Panacea hissed the word.  ``Don't you fucking \emph{dare}.''



``\ldots{}This time you got \emph{consent} before you screwed someone up beyond your ability to fix it.''



``I'll fucking \emph{kill} you,'' Panacea snarled.



There was a distant rumble, intense enough it could be both heard and felt through the doorway that Doormaker had open between us and Earth Gimel.  The fight was ongoing, and it sounded like maybe they were leading Scion away from the settlement.



My friends were out there.  Rachel, Aisha.  Here I was, doing nothing.



My hand slid on the stone beneath me as my body tried to push itself to a standing position, only to meet the `v' of bone at my neck.  Why had I done that?  I hadn't actually made the decision.



\emph{Passenger}?  I thought.



Was it making decisions with my \emph{body}, too?



Not a question I could answer definitively.  I turned my mind to a question I \emph{could} focus on.



\emph{Sixteen feet. }



I saw how the others were spreading out, forming a line behind Marquis, their attention on me.  I saw the length of the column of bone.



It belatedly clicked.  Sixteen feet was the distance they needed to keep from me.



``I'd like to say I'm sorry for being a little rough,'' Marquis said.  ``I was in a hurry, trying to get my daughter to safety.''



``\emph{Aahheuuhhhmmm.}''



It took me long seconds to wrap my head around the fact that the sound had come out of my mouth.  Not the right syllables, not even something that sounded like \emph{words}.  My hand flew to my mouth.  My fingertips dug through the thick spidersilk fabric for some purchase on my lips, as if I could somehow manually get them to start working again.  Even the movement of my hand was clumsy.



I was a puppeteer trying to make the puppet move by tugging the strings from some remote place.  Something as complex as speech was beyond me.



I tried to form words with the swarm, to speak or to spell.  I failed.



Far, \emph{far} beyond me.



I could see Tattletale reacting too, her entire body going rigid.  She took a half-step back.



I lowered my eyes to the cave floor.  My fingers were moving, grasping, and it wasn't me doing it.



``Ah,'' Marquis said.  ``Shame.  A communication problem makes it harder to gauge how much we can trust her.''



\emph{Trust her}, he'd said, instead of \emph{trust you}.  Like there was no point to saying it to me directly.  Marquis was talking to Tattletale to refer to me in the same way someone might talk to the family member or companion of a mentally disabled individual or small child, instead of the diminutive individual themselves.



As though I was so fucked up I apparently needed a \emph{guardian }to act as a translator or advocate.



``I can tell you how she is,'' Tattletale said.



``You're biased, to be frank,'' Marquis said.  ``I'm not willing to put myself, my family, or my underlings in a dangerous position because you have a sentimental spot for Weaver.  And before you launch into a spiel, I should warn you that Amelia here has filled me in on you.  I'm aware of how convincing you can be.  Spruce, Cinderhands, Lung?  You have my permission to mutiny if you think she's gaming me.  I even \emph{recommend} it.''



``Hardly fair,'' Tattletale said.



``It's rather fair, all things considered,'' Marquis said.  ``If you can convince \emph{all} of us, then it must be a legitimate and sound argument.''



``I think you're underestimating how eager Lung is for an excuse to hurt something,'' Tattletale said.



``Maybe so,'' Marquis said.  He glanced at Lung.



``You are too soft with women and children,'' Lung said.  ``If she starts something, I will break your rule for you and \emph{immolate} her.''



``I suppose that'll do,'' Marquis said, sighing a little, he gave Tattletale a look, and she nodded a little.



There was another distant rumble.  A sound like a thousand men screaming in unison.  I felt a chill.



``Let's put this issue to rest,'' Marquis said.  ``A compromise.''



``Sure.  I'm open to compromise,'' Tattletale said.  ``Beats being immolated.''



Marquis turned.  ``Doormaker?  Another portal, please.  We'll change locations and set up a triage unit somewhere else.  We link it to Gimel, and we close all doors leading to and from this cave.''



``I'm not sure I like this compromise,'' Tattletale said.



``Weaver is an unknown quantity.  We'll leave her here, as safe as anyone on any Earth is, and we conclude this fight against Scion, win or lose.  When all's said and done, we come back and we see what we can do for her.''



There was a long pause.



\emph{Stay here?  Not participating?}



I tensed.  My bugs stirred.



Right.  I still had my bugs.  My control was down, but only \emph{just}.  Anything I touched or manipulated would be like I was using my left hand instead of my right.



Problem was, I didn't exactly have a wealth of bugs to work with.



``It's\ldots sorta hard to argue with,'' Tattletale said.  ``But I don't like it.''



``Nature of a compromise is that it leaves everyone more or less equally unhappy,'' Marquis said.  ``I'd feel happier if she was under secure restraints, but I'm content to break this rod and leave her free to forage and look after herself while we're gone.''



No thread left.  I'd used too much of it when we'd made the platform back at the Cauldron base.



There was a new dimension to my power, at a cost to everything else.  Sixteen feet of range.



I just needed to figure out how to use it.



Tattletale shook her head.  ``If Doormaker dies, she's stranded here, all alone, more than a little borked in the head and in the heart.  Possibly for the rest of her life.''



``If Doormaker dies, I think we're \emph{all} in dire straits,'' Marquis said.  ``This is the fairest solution.  I think you realize that.''



I raised my hand, fingertips going vertical, moving my stump in that general direction, knowing she could draw the conclusion.  Best I could do in terms of a pleading gesture, with only one hand to work with.



Tattletale stared.  ``\ldots{}Yeah.  Except for one thing.''



``There's a snag,'' Marquis concluded, sounding a little defeated.



``Sure.  Life isn't fair, and I've got a hell of a lot of faith in that girl.  Besides, we agreed not so long ago that we wouldn't leave each other behind.''



``Unfortunate.  Lung, Cinderhands?  Make Tattletale leave.  Drag her if you have to, but don't hurt her.''



``You test my patience with this gentleness of yours,'' Lung growled, but he took hold of Tattletale's arm with one claw.  Cinderhands took her other arm.



``Watch for her gun.  If she gets a hand free, she'll use it on one of us,'' Panacea said.  She followed the trio.



I struggled to reach my feet, but the `v' of bone at my throat held me.  I slumped back down to the ground, staring at the ones who remained.



``Stop struggling, Weaver,'' Marquis said.  ``Please relax.  You took a gamble and you lost.  You sit this one out.''



I narrowed my eyes behind the lenses of my mask.



``Spruce?  Can you use your power?  Not too much.  Enough she can break free before too long?''



The tidy man shook his head.  He turned his hand over, and a little sphere swirled in it, looking like a cabbage made of stone.  He closed his hand, and it winked out of existence.  ``Ten years ago?  Sure.  Right now?  I don't trust my accuracy.  I'd be worried about the structure of the cave if my power touched anything to either side or behind her.''



Marquis nodded.  ``Go look after the others, then.  Be ready to shut the door the moment I'm through.''



Spruce turned to leave, ushering Doormaker and the clairvoyant out.



``I know you have tricks up your sleeve.  You have bugs, you have the pepper spray.  You have other tools I probably don't know about.  I'm going to assume you're in a state of mind to use those tricks.  I'm going to hope you're in a state of mind to listen when I ask you not to use them.  Stay here, pull yourself together, and we'll come for you when we can.  \emph{If} we can.  I give you my oath that I'll do my utmost to keep Tattletale safe in the meantime.''



My hands were clenching and unclenching.  Not by my own volition.



``\emph{Eeeeuunnh,}'' I growled.



``I'm very optimistically going to take that as a reluctant \emph{yes},'' he said.



It took me a moment to get the motions in order, but I managed to shake my head very slowly from side to side.



``Alright,'' he said.  He put an arm on Canary's armored shoulder.  ``Canary?  Please step through.  I'll be right behind you.''



She started to obey, then stopped.  ``I\ldots I really know how you feel, Weaver.  Sort of.  I took Cauldron's stuff, it messed me up, physically.  I felt horrible, I went a little crazy.  And maybe three years after I picked myself up and pulled it all together, everything went to shit.  Like life was reminding me of the mistake I made.  So I- I know what you're feeling.  But you \emph{can} make peace with it.  So\ldots don't beat yourself up too hard?  Take it from someone that's done that too much.''



``It was kind of you to say that,'' Marquis said.  ``Please step through?''



Canary nodded.



He was watching her go.



I heaved myself sideways, freeing my left arm to reach to my right hip.  In the process, I managed to move the branch of bone a little to one side.  Not enough to get my head free of it, but enough to get some elbow room.



``Heads up!'' Marquis called out.



My hand fumbled for my gun, and I pulled it free.  I raised it to the point where the branch split in two and fired.  The thickest point.



Perhaps a little insane, to fire upwards, at something as hard as bone, inches from my face and throat.



But the bone shattered and splintered.



I was free, and Marquis was already taking action.  Armor of bone surrounded him, ornate, decorative, but with enough coverage that the bugs near him were either crushed against his skin or they failed to find a way through.  I didn't have any bugs small enough to fit through the vertical slits around the eyes and mouth.



The spear of bone began branching out, becoming a veritable \emph{tree}, filling the cave between myself and Marquis with forking and dividing limbs.  He was backing away, creating more bone to stay connected to the base of the tree.  He knew what I'd try to do next.



I didn't stand.  I couldn't afford to take the time.  I used the flight pack, extending the wings with the thrusters, and launched myself at the wall of the cave.  I hit it a little harder than I might have liked, one wing bending, and then scraped against it, flying in Marquis' general direction, moving along the cave ceiling where there were less branches.



The amount of space I had to maneuver in was rapidly closing. My dangling leg caught a branch, and I nearly lost all of my momentum.  I was forced to put the thrusters away, but one didn't fold away properly where it had bent in the collision.



Tree branches of bone closed around me.  I activated the thruster on the remaining wing, and I opened fire, blind, in the hopes of clearing a route.



Marquis moved to the side, creating a shield of bone in front of himself and Canary.  The bullets weren't really on course for them, but it worked out in my favor.  He'd broken the shaft of bone to free himself to move, and the `tree' was no longer growing.  I flew through the biggest available gaps, snapping the thinner spears and spines of bone on my way through.



Twenty feet away from Marquis.  He moved back, and then grabbed the `tree'.



A disc of bone unfolded in front of me, as though the tree were a parasol.  A wall, a barrier.



I shot at the edge, and a chunk broke off.



But more flowed free before I could wedge myself into the resulting gap.  It sealed the cave off.  I shot again, but it was too thick.  The trigger clicked as I pulled it again and again, fruitlessly.  The movement was so frantic and jerky that the gun fell from my clumsy grip.



``Terribly sorry,'' Marquis murmured.



Panic and fear welled up inside me.



\emph{I don't want to stay behind.  I can't.  You don't understand.  I'll lose my mind, more than it already feels a little lost}.



``\emph{Gorrugh,}'' I hissed.  The armor of my mask clicked against the bone as I rested my head against it.



The fear, the panic, no\ldots



I felt it, but it wasn't \emph{mine}.  Neither was the fear and paralysis I'd felt before, or the anger.



I was so used to my power being automatic, I wasn't used to having to exert any kind of \emph{will.}



I tapped into the feeling, I focused all of my attention on my ability.



Sixteen feet.  Marquis was out of my range, but Canary had been slower to move, her reflexes not as good.  She'd been caught up in \emph{watching, }maybe not wanting to turn her back on a fight in progress, and she hadn't moved as quickly.



I was touching the wall of bone, and Canary was fifteen or so feet away, on the other side.



Now that I was taking the time to \emph{look}, to \emph{sense}, I was aware of Canary's body in the same way I'd been aware of Lung's.  As Panacea's, to a lesser degree.  Her steady, measured breathing, the complete lack of movement.



Just like Lung and Panacea had been frozen.



Waiting for instructions.



I couldn't move her closer to Marquis without putting her outside of my range.  Instead, I turned her around.



``Ah\ldots damnation,'' Marquis said.



Her movements weren't much more fluid than my own ones here.  A drawback, among many.  She marched towards me and the wall Marquis had created.



He snared her, throwing out shafts of bone and surrounding her upper body with a cage of the stuff, interlocking the two pieces.



But she wore the Dragonslayer's armored suit.  She bent her legs at my order, and then lunged forward.  She broke the bone that surrounded her, and with her fist free she struck the wall of bone.



Two, three, four times.



Marquis stepped forward, very carefully, and planted a foot on the base of the shaft of bone.  The wall began to thicken, faster than Canary could smash it.



Her power\ldots



I \emph{looked}, and I had enough of a sense of her inner workings to get a sense of her general state of well being, where she was sore, her fitness, and her power.



She began to sing.



\emph{Bring him closer.  Bring him in}.



The song \emph{changed}.  The relentless, almost machinelike drum against the wall of bone continued, cracking it with the power of the suit, and I could sense Marquis wavering.  He lowered his foot from the shaft of bone and began to approach Canary.



I was so used to a buzzing, to a dull roar of power in my ears.  This was so much more complex.  Complex and seductive, the emotions I was tapping into.  Linking myself to Canary on some level.



I could remember being in Dragon and Defiant's grip, being hauled along on the way to the roof, so soon after killing Alexandria and Director Tagg.  Struggling, futile, hopeless.



I could look beyond that surface memory, and I could see what was beneath it, a general sensation, a recollection of a feeling.  \emph{Canary, }struggling, helpless and bound, terrified and panicking, with a dull sense of guilt over what she'd done, a reality that she hadn't quite processed and might not fully process for weeks or months.



She was me and I was her.  Shared experience.  She was an extension of myself.



There was no way to know if that was a good thing.  I was starting to feel a little unhinged again.  A little disconnected from \emph{me}.



The only thing scarier than that fact was the knowledge that it was only going to get worse.  \emph{This} was my tool.  This was what I'd sacrificed my mind, body, range, and control to obtain.  Sixteen paltry feet of range.  Sixteen feet of range that, according to Panacea, I wouldn't be able to increase through my emotions.



I made myself climb to my feet, pushing my way through the smaller branches of bone, reaching up with my hand to grab a larger branch for balance.  My legs were shaky beneath me, my head a little lopsided, and if I hadn't been holding on to something, I suspected my arm would have hung utterly limp at my side.  I couldn't\ldots I couldn't \emph{dig} for that knowledge of how my body was supposed to be in a resting state.



I saw the first crack spread on my side of the wall.



Better yet, Marquis was getting closer.  One or two more reluctant steps our way, and-



-And I never got to find out if I'd be able to leverage his power.  Lung stepped into the hallway, and he filled it with fire.



Canary was armored, though her hair was set on fire where it flowed beneath the helmet.  Marquis, too, was armored.  Neither was positioned to be turned into a crisp.



But the fire drowned out the singing.  The fire stopped, and Canary could hear Marquis' footsteps as he ran, hands pressed to where his ears were covered by his helmet.



I had Canary punch through the wall.  She reached through the wall and grabbed me by the straps of my flight pack, hauling me through.



The doorway was closing.  Canary, it seemed, was being left behind.



I had her throw me, and I used my flight pack to get extra speed.



I slid through the doorway two seconds before it was too narrow to pass through.  I lay there, the group staring down at me.



``\emph{Coohugggah},'' I mumbled, with more than a little anger in my voice, as I slowly made my way to my feet.  Nobody offered me a hand, but that was my choice, not theirs.



My stump of an arm was throbbing, and the rest of me felt alien.  My movements weren't all my own choice, with the passenger apparently doing something to help me manage.



I looked through the \emph{other} portal, beside us.  Gimel.



I left the others alone, not controlling them.  When Spruce was in my way, I pushed him aside with physical strength.



\emph{I'm fighting}, I thought.  \emph{I'm fighting Scion.  Somehow}.



I could see myself through their eyes.  Each image was slightly distorted, just different enough to be uncanny and out of sync.  I had more awareness of myself through them than I had with my own eyes.



I stepped into the damaged fast food restaurant, and over the rubble at the front where one attack or another had clipped the building.  As I made my way to the front, the others behind me found themselves out of my reach, free to move of their own volition again.



Free to attack me if they wanted.



Marquis, Panacea, Bonesaw\ldots not so dangerous.



Lung?  No.  If he was going to kill me, he'd let me know just before he did it.



Spruce?  Cinderhands?  They were maybe the type to attack me, because of pride and the fact that I'd momentarily seized control of them.



Tattletale was freed.  She dashed forward, hopping over rubble and debris to get closer to me.  She stopped three or four paces from me.



A fraction more than sixteen feet away.



But she didn't say a word.



Scion was there.  Tearing through people with a \emph{ferocity}, this time.  People were scrambling for cover that did so very \emph{little} against Scion, trying to erect defenses, hiding and fleeing.



Had we already lost?



A collection of capes, many carrying wounded, headed our way.  Rachel, Imp and Bastard were among them.



I moved to the side, but I failed to anticipate their path.  I'd expected them to head into the sandwich-place-turned-hospital, but they moved straight towards me.



I backed away, taking flight, while Tattletale rushed forward, her footfalls tracing a curved path around a bubble that only she seemed to be conscious of.  She stopped in their way, arms outstretched, shouting, ``Go around!  Dangerous power!''



Most of them listened.  Only one, looking over his shoulder at Scion, stumbled past Tattletale, into my range.  I was looking for it this time, and I could feel his \emph{being} snap into my mind's eye.  He froze in place.



No sooner did I have control than Tattletale grabbed the guy by the back of the collar and hauled him out.



``The fuck?'' Imp asked.



Tattletale let the guy go, and he fled.



I couldn't reply, so I focused on gathering my bugs.  No use dismissing a resource that had once been vital.



``\emph{Someone} volunteered herself for noninvasive brain surgery from the lunatic with a sister complex.  Or, just as likely, she asked the lunatic psychopath for \emph{invasive} brain surgery and the other lunatic stepped in.  Now Skitter's broken.''



``That didn't \emph{look} broken,'' Imp said.  ``That guy\ldots''



``Hrrrrrn,'' I said.



``Hrrrrn,'' Imp replied, nodding sagely.  ``\emph{Now} I understand.''



``She can't talk,'' Rachel said, more a statement than a question.



I shook my head.  \emph{Can't move as fast or as well as before\ldots}



I belatedly realized that Rachel had hopped off of Bastard.  She reached her hand forward, as if feeling her way.



I backed away, but she stepped forward faster.



A conception of Rachel's entire being bloomed in my consciousness.



I made her step back away.



``Mm,'' Rachel grunted.



``Why the fuck would you do that?'' Tattletale asked.



\emph{Because she trusts me far too much, }I thought.



``She's smarter than I am,'' Rachel said.  ``Let her do what she needs to.''



I shook my head, backing away with my flight pack.



Controlling Rachel wouldn't achieve anything.  I wouldn't get any special knowledge of her whistles or commands, or her instinctive understanding of the dogs.



But I needed to do \emph{something}.



Marquis and the others were approaching, on guard, looking tense.



I was a wild card, now, something they couldn't wholly trust.  A little unhinged, a little unpredictable, and my power would be more dangerous and debilitating in their minds than it was useful.



``You're going?''  Tattletale asked, almost realizing it before I had.



I nodded.



``Good luck,'' she said.  ``You know where to find us.''



I nodded again, taking to the air with my damaged flight pack, but it was with a heavy heart.



I'd told myself, not so long ago, that I'd know the route to victory when I saw it.  I had an idea of what I needed to do now.



Maybe it was good I couldn't speak, because I would've said the words if I'd had the ability, and we'd sworn not to.  I had to think it instead, and this way, they didn't need to hear it.



\emph{Goodbye, Undersiders.}





