





We were broken, routed.



When had it happened?  When had we reached that critical juncture?  Had one specific act or moment marked the point where the rank and file capes had stopped fighting and started merely trying to survive?



Morale was failing, and had failed long ago.  A good fifth of our fighting force here was made up of Nilbog's creatures and Dragon's suits, which self-repaired and kludged together with the remains of other damaged suits to return to the field again and again.  That was \emph{with} the reinforcements that were coming through Doormaker's portals.



Chevalier and Ingenue, the other Birdcage leaders and other teams were trying to gather into a defending force.  Issue was, there wasn't really a way to \emph{defend}.  Scion held the keys to all things power related, and any attack that didn't penetrate a particular defense needed only to be tweaked, adjusted with a moment's thought.  Following that, it passed through forcefields, armor and time distortions like they weren't even there.



The same was true in terms of our ability to \emph{attack}.  I had a sense of Scion's scale, because I'd seen his partner, and I'd gotten a glimpse of the sheer mass of the partner from how much had flowed through into our world as Scion had moved it.  I could assume they were roughly equivalent in size, and that meant we were trying to tear through \emph{landmass} of raw matter, and we were doing it a few handfuls at a time.



I could look at how durable the partner entity's flesh had been when Rachel and Lung had been tearing through it, extrapolate to the attacks we'd seen here.  We weren't doing nearly enough, especially if he was compartmentalizing the damage and keeping himself from losing more than a certain amount at a time.



To top it all off, anything we found that \emph{worked} only worked for a short time.  Either the user died, or Scion adapted his defenses to become immune to it.



I knew this.  A good number of us knew some of it, especially the ones who'd attended the meetings with the major players.



But for a large number of people on the battlefield, this wasn't all common knowledge.



For the others on the ground, this was a man with golden skin who didn't seem to be bothered in the slightest by the vast majority of what we were throwing at him.  At best, he seemed \emph{annoyed}, by effects as massive as the ones String Theory and Gavel had dished out.  At best, we gave him \emph{pause} for a moment.  He was toying with us in a way that made it clear he was holding back, yet it didn't take away from the horror of his actions.



It was impacting morale, instilling a kind of hopelessness, and that hopelessness was a big part of why things were falling apart before my eyes.



I saw him generate a beam so thin I couldn't make out anything but the glow around it, tracing it through a group.  It cut into throats, arms, legs and chests.  The wounded capes fell, all together.



Blood welled out from the cuts the beam had made in their flesh.  The damage wasn't lethal, not yet, but it was bad enough that death was likely.  Even inevitable.  I saw a trace of golden light on the skin around the wound.  The damage was spreading.  It wasn't the sort of injury a medic would be able to handle.



Sixteen capes in all, left to feel their hot blood flow free, their lives seeping away.  Not everyone Scion had targeted was in such bad shape.  One had dodged, pulling a teammate out of the way.  Another three or four had survived the attack by toughness alone, with armor and powers protecting them.



Scion moved, advancing on them.  One sphere of golden light, turning one of these hyper-tough capes into ash.  And then he was in their midst, hitting them with physical blows, tearing them to pieces, each hit harder, faster and more gruesome than the last.  A sweep of his arm and a cape with stone armor was torn in two.



Two or three seconds and he'd taken nineteen capes out of action, wounding several more.  But the \emph{real }effect was on others, on capes who were now giving up, trying to get away from this slaughter.



He advanced on the two who remained, and it was Chevalier who got in the way, slamming his cannonblade down, twenty feet long and eight feet high, a physical barrier in Scion's way.



Scion raised one glowing hand, not even slowing as he advanced towards his intended targets.  The sword, to Scion, was little more than tissue paper.



Which made it all the more surprising, to him and to me both, when he \emph{stopped}, his hand touching the barrier and failing to tear through it.



Chevalier drew the sword back, then \emph{cleaved Scion.  }The sword passed through the golden man's shoulder, ribcage, and out his waist, cutting into the earth.



\emph{Bisected.}



Chevalier remained where he was, hands on the handle of the weapon, making eye contact with Scion.  Ingenue was only a short distance behind him, looking more like she was dressed up to go to a club than to be on a battlefield, with a little leather jacket and a dress with the slit up one side,  her hair draped over half of her face.



Just the same as we'd seen with the Siberian.  The damage was there, but Scion was holding himself together.



Scion withdrew himself from the sword.  Chevalier slashed again, slamming Scion into the earth, then used a sweep of the sword to vault himself back.



\emph{Scion's a ghost, it's a mask}.



\emph{And whatever Tattletale says about him being human at his core, human on the surface or whatever else, he's a natural disaster, not an individual.}



\emph{A force of nature.  Impossible to control or prevent.  }The words crossed my mind, and they were \emph{my} words, but they weren't my thoughts.



\emph{Reminding me of the bad old days, Passenger}?  I thought to myself.  My bugs continued to gather around me.  A familiar and comfortable presence, considering everything that was happening.



\emph{I'm not giving up!}  My voice, sounding so far away, even in my own head, so young.



\emph{Damn straight}.



Chevalier blocked Scion's beam with his sword, then moved the blade, pulling the trigger.  The cannonball hit Scion, and knocked the golden man back.



Capes were taking the opportunity to flee.



I knew what I had to do, here.  Even with a myopic, skewed perspective.  I could guess what the ultimate price was going to be.



Maybe a good part of myself was a monster.  Maybe a part of me was still that girl who had very nearly gone on a rampage in her school, still that girl who would have been an angry, frustrated, aimless c-list villain, a footnote in a footnote in the grand scheme of things, forgotten by nearly everyone once the media frenzy had died down.



\emph{The hell am I supposed to do!?}  The memory was so clear I could almost hear my own voice.  Had that anger ever really gone away?



The world didn't fucking make sense.  \emph{People} didn't make sense.  I'd been railing against it from the beginning.



I dropped to the ground, cutting one of the boosters to the flight pack.  I didn't position my legs right, and I folded, landing on my knees and hands instead of on both feet.



I felt a spark of fear, then another.  Capes stopped in their tracks, and the ones behind them crashed into them, driving them forward, some toppling onto a disc a tinker was riding.  Seven people, now inside my range.



I could get a sense of their powers.



The disc the cape was riding was a tinker device, hovering over the ground with a constant stream of air that sent dust billowing in low rolling clouds around the edges.  A woman rode the platform, garbed in a green, flowing kimono-style dress, surrounded by some sort of tinker-derived cyborg bonsai trees on raised sections of varying height.



I began to find my feet, using both my hands and the flight pack to get myself upright.



I could feel the tree-girl's fear, the fact that she was cornered.  It was echoed across each of the seven who'd stumbled into my power's radius, and it invoked memories.  Different memories for each of them.  For \emph{her}, it called Leviathan to mind.  Me running, being struck from behind.  There was one case that reminded me of being with my dad in the room, wracked with shame and helplessness, a complete and total lack of direction.  Another that, inexplicably, brought up the scene with Dragon and Defiant in the Arcadia High cafeteria.  A sense of injustice, mingled with surrender.



For another, for \emph{two} others, it brought up Mannequin, but they were different scenes.  Being in the empty factory with the innocents at the edges, a building rage, and being there when he'd attacked my territory the second time, after we'd saved Amy.



In both of those cases, it was the same kind of rage I'd just been thinking about.  To these two, I was the freak of nature standing in their way.



I was broken, and I'd bitten off more input than I could chew.  The passenger was tapping into the experiences it had shared with me, because that was the only way it could convey the signals I was getting from them.



Which wasn't what I needed.  It was the wrong inputs.  What I \emph{needed} was to decipher their powers.  The tinker with the trees\ldots I could sense things about her that \emph{weren't} tapping into memories I understood.  Something mental that I couldn't relate to, out of my reach.



I ordered them to turn.  When they moved, they lurched.  Unfamiliar proportions, different degrees of athleticism.  Like my adjustment to my new arm and legs.



Could I get used to moving them like I'd gotten used to the new limbs?



Laughter disturbed me from my thoughts.



``Human shields?''  A man asked, almost unintelligible with his coarse accent.  ``I love it!  I was ganna shoot the bloody idjits in the backs, you're `lowed to do that, `miright?  But some cunt might get the wrong idea.''



When I turned my head, all but one my minions turned their heads as well.  My fault.  I'd wanted the extra sensory input, and I'd instinctually tried to take it in with a share of my `swarm'.



It was Acidbath.  One of the Birdcage's cell block leaders.  He had the stylings of a rock musician or punk rocker who'd spent a little too much time doing drugs and not enough time playing his instrument.  Worn around the edges, a little too full of himself.  He'd been a bit player in the real world, caught up in his vices, yet had managed to take over and rule a cell block for three years after being sent to the Birdcage.



He was still smirking, laughing a little, as he looked between me and Scion's ongoing fight with Chevalier.  He danced a little from foot to foot, tensing just a bit every time Scion moved.  Not out of fear.



\emph{``This }is better,'' he said.  ``They wanna run and leave us assholes to do the fighting, you can say otherwise.  Pin 'em up and let Scion knock 'em down.''



\emph{No.  They aren't meat shields.}



But I couldn't tell Acidbath that.  I couldn't answer him because I couldn't communicate.



It galled me that he thought I'd use them as cannon fodder.  Not least because he was right.  \emph{Partially} right, but that didn't make it much better.



I'd compared myself to some pretty horrible individuals in the past, but Acidbath was something else.  He was \emph{low}, barely above dirt.  He'd scalded his own brother with acid, and had gone after girlfriends and girls who had rejected him.  The attacks hadn't been lethal, but had melted flesh and the fat or muscular tissues beneath.  I'd seen the pictures of the aftermath when I'd browsed his files, after the scar tissue had formed.



I couldn't think of worse ways to hurt someone, and he'd done it in impulsive acts of retaliation.



If I was going to be a monster, I'd at least try to be smart about it, constructive.  To have a \emph{plan}.



I set my new minions into action.  I couldn't get too caught up in the details.  Their powers were a part of them like the venom was a part of a spider or centipede, or web a part of the spiders I controlled.  I had to take it in without getting caught up in analyzing it, trusting the passenger to handle the essential details on autopilot.



As my new minions rejoined the battle, I felt the tinker tap into that power that had previously been out of reach.  I got a glimpse of how she operated, the world she saw; a distorted world much like I'd seen when I tried to look through my bug's eyes.  The trees were primed and loaded like guns.  Tinker-herbalism, only it wasn't very medicinal at all.



I set her aside.  The others\ldots my passenger was better at controlling most of them.



A cape in a black flowing costume who had powers I couldn't decipher.  I set him aside as well.



The others were easier to use, and I wasn't sure how much of it was because of their powers' similarities to my own.  Focusing on them resulted in a deluge of fragmented memories, memories of me using my power in different ways.



Two shaker-classification capes provided the majority of the offensive power.  If I let them be, if I let things move on autopilot in their own way, then they used their power well enough.  A telekinetic with an emphasis on small objects, with a storm of ball bearings and small stones from the road, and a cape that could create superheated shafts of energy, anchoring them between two objects.  The memories were of my bugs attacking as a coordinated whole, of the threads I'd extended as tripwires and my attack on Echidna.



Not that I was so graceful or effective in using their abilities.



There was a woman, and focusing on her resulted in a deluge of fragmented memories, but these were memories of using my bugs to \emph{observe}.  A secondary power?  Trying to tap into her \emph{other} power resulted in thoughts of Atlas, the void in his midsection, of my relay bugs.  Something incomplete?  A kind of frustration.  With my eyes, I could see her fingertips glowing blue.



I moved her hand, and I saw a line drawn in the air.



\emph{Something incomplete}.  I moved her hand in a circle, and I closed the line.



There was a small pop as the space we'd enclosed disappeared.  My bugs could feel the air moving at the destination point.



A teleporter with a somewhat irritating limitation.



The other two looked like members of the Birdcage.  Very possibly Acidbath's underlings, though he hadn't identified with them.  Brutish, mean looking.  One was armored in what looked to be fragmented pieces of pottery and glass, with flesh webbing between fragments, while the other was covered head to toe in biker tattoos, oddly doughy looking, with a power that was being channeled just under his skin.  Focused air.



Alexandria joined the fight, relieving Chevalier, who was on his heels, his blade in rough shape.  A third cape I didn't know joined the fight.



Scion shook off the pair, and then struck Chevalier hard enough to send him crashing into the crowd opposite us.



Then he wheeled around.  His eyes passed over Acidbath.



Acidbath, still dancing from foot to foot, leaped, and he changed into a living tidal wave of clear liquid, isolated, with roughly five times his mass.  He materialized into regular human form when he was a little behind and to one side of Scion, and then lashed out, slinging punches that ended with his hands becoming liquid projectiles.  They splashed against Scion, and I could see smoke rise, even though there wasn't any visible damage.



If Scion had been planning to attack us, the cape with Alexandria managed to get his attention.  Another flying bruiser type.  An `Alexandria package' cape fighting alongside Alexandria herself.



Or Pretender, whoever.



The fear that was emanating from my minions was paralyzing me, I realized.  I shook it off and stepped up the attack.  The one with the shards and the one with the soft looking body charged to either side, and moved right out of my power's range.



I \emph{hoped} they would take this as a nudge, a push to get back into the thick of things.  Both these capes and the ones around us.  We weren't many, but we were a little closer to Scion than most, and we were steadfast.  Capes who were backing away on either side of us were keeping their eyes on Scion, where they might otherwise have routed completely.



The guy that was made up of fragments took the nudge from me for what it was, giving me a hard look over one shoulder before he joined Alexandria and the other cape in attacking Scion.  He was a shapeshifter, maybe one like Mush, from the Brockton Bay Merchants.  My assessment of his power suggested he was tougher than he looked.



The other one, with the air swirling beneath his skin, simply left my range and ran.  He found a spot with more capes and slowed down, dropping into a crouch, like he might run at the first opportunity.



Scion threw the Alexandria-package cape I couldn't name into the ceramic shard guy, and he managed to break the cape's fall, falling to pieces in the process.  He began picking himself up, gathering more pieces of glass from nearby rubble to make himself bigger than before.



Acidbath stepped up the attack, slinging acid every time the path was clear,



I didn't want to lose my stride, getting caught up in observation.  I focused on my minions.  The tinker with the disc had her plants loaded down with drugs.  I focused our attention on different things, and I got more fragmented memories in response.  A glimpse of me, paralyzed, with Bonesaw about to operate on me.



\emph{Poison?  Paralytic?}



Being inside the building Coil had set on fire.



\emph{Incendiary?  Blinding?}



The hospital bed-



I was acting even as the knowledge came to me.  I pushed her to use that one, and the passenger took over.  It was better at understanding the abstracts.  I could follow what it was doing, grasp the basics of it.  Her body and the seat beneath her was another plant, focused on producing, concentrating and storing gases in a combination that served as breathable air, the same gas that was keeping her disc aloft.



Her hand moved, the raised platforms shifted, and one tree was lowered to a point just in front of her.



The gas blew what looked like a vast cloud of purple pollen out onto the battlefield.  It settled on the wounded capes, and only the wounded capes.



\emph{Coagulants}, I thought.  \emph{Painkillers.}



I watched the others carefully, making sure that my minions weren't inadvertently putting others in the line of fire.  I started circling our group with our teleporter, drawing out a line as she jogged in a tight loop.  The two shakers, the telekinetic and the guy who made lasers, they had matching costumes.  Had they combined their techniques?  I formed lasers between the airborne ball bearings.  Needle thin, they still cut into Scion.



The damage of one with the flexibility of the other.  No doubt a technique they'd used on their own.



Scion turned his head, looking at us.  His hands glowed.



The teleporter lunged forward, completing the loop, leaving out only the brute with the weird skin, the fragment-shapeshifter and the girl with the disc.  I gave one last command to make the disc-botanist tinker start running.



Our group was collectively teleported away.  I could feel the strength drain out of the teleporter to the point that she fell to the ground.  Scion's attention was elsewhere.  He hadn't gone after any of the ones we'd left behind.  We'd managed to avoid his attentions.



I turned my attention to the one cape I hadn't yet figured out.



A voice interrupted me.  ``Queen Administrator.  I almost didn't recognize you.''



\emph{Glaistig Uaine}.  I didn't respond.  My focus was on the young man.  Some kind of trump power, responding to a few glimmers here and there.



I turned her way.  She was dressed in a complicated dress of green-black ribbons, complete with a hood.  \emph{She looks so young}.



I pointed at the cape I was trying to figure out and raised my stump-arm in a shrug.



``If you want to get a full understanding of your new capabilities, you must figure that out on your own,'' she said.  ``Practice, and it will soon be second nature.''



I turned my attention to the cape.  My focus, again, was interrupted by her voice.



``I will warn you, do not attempt to usurp me.  If I catch you trying, I will fight you.  I am careful to tend to my flock, and would not have anyone but me handle them.''



I nodded.



``Good.  Peace is preferable,'' she said.  We watched Scion unload on another group.



\emph{They can't stop him with brute strength.  They know it.  Yet they keep coming.  Is it just for the sake of going out with a fight?  The hope of finding some trump card?}



I'd stopped capes from running, but the idea wasn't to stop \emph{retreat}.  Retreat was sensible.  I didn't want things to devolve into a panicked stampede to get away.



``It seems we're losing, Administrator,'' Glaistig Uaine said, as if echoing my thoughts.



I shook my head a little.



``I would offer him solace, if I knew how.  He is in a dangerous state, and I find myself worried for the first time.''



I glanced at her.



``Yes, very worried.  Had things gone like they were before, I would be bothered, but not overly \emph{upset}.  We would die, the faerie would slumber and they would wait.  With luck, with a \emph{great deal }of luck, \emph{he} would find another partner, or another partner would find him, and things would be set for the great play to start anew, on a fresh stage.''



Scion had stopped with the beams and the blasts.  He was throwing punches again, hurling himself into the thickest parts of the crowd.  Nilbog's creations were taking the brunt of the attack.



``But the faerie are creatures of whimsy, aren't they?  Easily influenced by the masks they wear.  It's the whole point of them, isn't it, Administrator?  It's why they \emph{are}, yes?''



I nodded a little.  I could almost see it.



She nodded a little herself, as if satisfied by my response.  ``\emph{He's} fallen prey to the worst kind of whimsy, a destructive wroth.  He is heartbroken and hopeless, he has lost more than you or I could ever imagine, and he may well leave this stage so ruined that things cannot be salvaged, unless we're fortunate enough to get a\ldots''



She trailed off, grasping for a word.



\emph{Understudy?}



``Fortuitous arrival,'' she said.  She smiled a little.  ``Not very likely.  They litter breadcrumbs in their wake, not to be followed, but so their kin don't waste time and effort traveling the same paths.  For another to arrive here, they would need to avoid touching a single crumb, like you or me swimming the length of a river without touching a wave.''



Black Kaze had entered the battlefield, backed up by Dragon's Teeth.  She disappeared, and then reappeared behind Scion, katana drawn.  A moment passed, and Scion reacted as though he'd been punched dead center in the chest.



Not a big reaction, but it was \emph{a} reaction.



Black Kaze alternated attacks with Acidbath, very proper, measured in her movements, compared to Acidbath's flailing, reckless, hurried scramble to keep out of Scion's line of sight.  Acidbath moved with surprising quickness, faster than a typical car might.  A peculiarity of his breaker power.



Glaistig Uaine offered a small laugh.  ``I cling to a sliver of hope, and I know I'm fooling myself.  There really isn't much of a time window.  A few thousand years is \emph{such} a short time, you know.''



I continued to pay attention while I focused on the more mysterious cape in my range, the one who I hadn't deciphered.



The connections of his powers to something that was there but not quite there\ldots his power hinged on some outside qualifier or factor that wasn't being met on this battlefield.  It was concentrated most on the wounded\ldots



It snapped into place.  His power worked with people who were \emph{sleeping}.  The people his power \emph{sort of }worked on were unconscious.



I used the teleporter to draw a circle around him.  A moment later, he was gone, set in the midst of the biggest cluster of wounded.



``Ah, you understood.  Good.''



Only a moment later, Scion attacked, striking the ground.  We were distant enough that I could see the circle of golden light expanding around them, a ring that ripped through the ground, demolishing it.



Nilbog's creations, the defending forces and Dragon's suits were all toppled as the ground settled.  Buildings collapsed.



A wounded Leviathan emerged from the water, approaching Scion with an almost lazy slowness.  Capes practically fought one another to get their footing and get out of the way.  Some were too rough in their hurry to get by Nilbog's creations, only to get attacked by the things in retaliation.



I clenched my one fist.



``Would you accompany me?  We would be the queen of the living and queen of the fallen.  No swords in our hands, but warlords nonetheless.  Yes?  I will give you hints, if you desire them, and help you manage your soldiers.  One last hurrah, a great war to end it all, like the best myths have.''



I shook my head slowly.



``No?  A shame.  Fear?  A lack of soldiers?''



I shook my head, still.



``No, you are not afraid, queen, or you \emph{are} afraid, but this is a fear that drives you forward.  You have something you intend to do.''



I nodded.



``Then I will be here when you return, and we can have that great battle, fighting to drive \emph{him} back into slumber.''



I gathered my swarm around me and the teleporter, and I had her draw another circle.



Glaistig Uaine reached out, seizing the woman's wrist.  The teleporter's alarm mingled with my own.



But she wasn't attacking, and she wasn't taking the teleporter's powers, extinguishing her life in the process.



``A warning,'' Glaistig Uaine said.



I gave her my full attention.



``You sought power, and you lost a portion of yourself in the doing.  Always the case, but it's\ldots pronounced, in a case like yours.  Yes?''



``Hng,'' I mumbled.



``You will need a tether, an anchor.  It can be an idea, a physical thing, a place, a person, a goal.  Right now, it will not seem so important, but it \emph{will}.  When all is said and done, you will either be dead, and this thing will be a comfort to you in your last moments, or you will be powerful, and it will be all you have left.  Decide what you will hold on to.''



\emph{I've already decided what that is}, I thought.  Since \emph{a long time ago}.



``Choose very carefully,'' she said.  ``Take it from someone who knows.''



Then she moved the teleporter's hand, closing the circuit.



The teleporter and I arrived at our destination at the same moment Leviathan crashed into Scion.  Water mingled with the ruined landscape, seeping into cracks, making life just a bit harder for the capes in the center of the disaster area.



I felt memories stir.  The moment I'd announced myself as Weaver and heard the howling.



\emph{You really have to make this unnecessarily hard, don't you}?  I thought.  \emph{Reminding me that I'm abandoning them}.



Yes, Rachel and Imp were probably there.  So were the capes I'd controlled and urged back into the fray.  Maybe they had turned to run at the first opportunity.  Maybe they had been given a chance to reconsider, and were still fighting.



Maybe I'd killed them, by denying them the chance to run.



But I told myself I wasn't abandoning them.



I had a mission, and this was a mission that would take me back to them, after a fashion.  I might never rejoin the group, I was fully aware of what I was getting myself into, but this was for their sake, not \emph{despite} them.



That detour was a part of the mission, killing multiple birds with one stone.  Helping to stop the rout, trying to do a little something to keep the fight going, so the capes on the ground could buy time.  Learning about my new ability, testing my ability to accommodate unfamiliar abilities.



It hadn't been planned, so much, but I'd also had a reminder of something that had slipped my mind.



Glaistig Uaine was one of my most dangerous enemies at this point.



Now I was in dire need of information.  Getting that information was a surprising obstacle, considering my inability to communicate.  I couldn't \emph{ask}, couldn't whip out my phone and type something into the search bar and wait for it to dig records out of the archives.



To these ends, I'd moved us to the edge of the settlement, where six armored suits were deployed and waiting to be sent into the fray.  The Pendragon was one.  Dragon's Teeth were scattered throughout the area, many holding what looked like rocket launchers with glass bulbs at the front.



The teleporter was exhausted from using her ability, and leaned on me as we made our way forwards.



D.T. officers stepped forward to bar my way.



Alarm, surprise.  I was momentarily dazed by images of a number of surprise attacks and explosions.  My power had reached them, and they stepped aside at my command.



I moved as confidently and as quickly towards the Pendragon as I could manage, trying not to show fear or uncertainty.  Harder than it sounded, given my limping, uneven gait, and the way my head slumped forwards.  D.T. officers beyond my range took notice and moved to flank me.



I reached the back of the Pendragon and I slammed my hand on the metal door.  I did it again.  My best attempt at a knock.  I tried my best to stand straight, folding my hand behind me.



Not quite loud enough.  The armor was too thick.  Still, the fact that I'd knocked was a point in my book, as far as the officers were concerned.  They were hanging back.



``Defiant isn't replying,'' one of the officers said.



``Try Dragon,'' another spoke.  ``She always answers calls.''



``Ladies!''  One called out.  ``State your identities for the record!''



\emph{You know who I am}, I thought.



``We know your face, we've met, but we can't take anything for granted here!  Stranger and Master protocols are in effect!''



\emph{Oh}.



Were the protocols in effect because of me?



Or was it a problem that stemmed from the half-dozen incidents in the last two years, where people had tried to capitalize on Endbringer attacks and other crises, attempting assassinations on key figures?



I couldn't argue it, in any event.  I couldn't defend myself, either.



``Both of you!  We'll need your names, and we need at least one good password!''



Right.  Lovely.



Couldn't use the teleporter without getting shot.  They'd see the line\ldots



Unless they couldn't.  Seeing myself through the teleporter's eyes, I was a little surprised at the sheer number of bugs I'd accumulated.



She moved her hands to me, and she drew the line through the middle of the swarm.



Could she teleport where she couldn't see?



I focused our attention on the interior of the Pendragon.



She closed the circuit, and we were inside.



My bugs could sense the soldiers reacting.



``Weaver?''  Dragon asked.  ``I was just about to step outside.''



I stepped away from the teleporter.  My eyes roved over the ship's interior.  Less elbow room than in the Dragonfly.



``Tattletale filled me in, asked me to pass on the details,'' Dragon said.  ``A lot of people are worried, here, on quite a few different levels.''



I couldn't respond, and I knew how tight time was, so I met her eyes, nodded a little, and then gestured towards the nearest laptop.



``Yes,'' Dragon said.  ``Of course.''



I gave her a little salute.  I didn't know a better way of expressing thanks.  If I'd known sign language, would I have lost it with my ability to speak and write?



``Tattletale was saying you were unfocused.  I'm not getting that sense.  You're up to something.''



The laptop booted.  I froze.



\emph{Oh.  Damn.}



I realized what I was looking at, and I felt my heart plummet.



When my mom had died, I'd sort of turned to books as a way of remembering her, a way of being with her in the present day, reminding myself of the nights she would read aloud to me, then the nights we'd read together, and beyond that, times when we'd all be in the living room, my dad with his computer half the time, a book the other half.  My mom and I always had our novels.  Sometimes we had shared, sometimes not.



When the bullying had started, books had been an escape.  I'd be exhausted at the end of the day, feeling a low that counterbalanced the higher adrenaline and stress of the time spent in school.  Curling up with something to read had been a refuge.



Maybe that had lapsed when I'd become a cape.  The costumed stuff had become an escape of sorts.  But I'd gotten back into it in prison, and on some of the stakeouts.  I'd taught myself braille, so I could read with my bugs, and take in more.



I would have settled for being a little crazy.  I would have settled for some physical impairment, for a power that was so out of control that I couldn't have real human contact again.



The words were gibberish.  I couldn't read.  It had been something I'd turned to in my lowest moments, a little crutch, a coping mechanism, and it had been denied to me.



It hit me harder than the loss of my voice, stupid as it was.  My hand shook, hovering over the display.



I watched as the words disappeared, replaced by images.  A composite picture of locations, a composite picture of faces, a composite picture of icons that no doubt included details on powers.  There were others I could scroll down to see.



My eyes watered a little.  I couldn't look at Dragon, but I raised my hand in another salute.  Not nearly as good a thank-you as I wanted to be able to give.



My fingers touched the display.  Faces.



There were sub-menus.  All visual.  I clicked the frowny-face with the black background, then the little map for a world map\ldots America.  I clicked the map icon again for a national map\ldots Washington.



I found Teacher's portrait near the top of the results list.  One of Washington's most notorious capes.  Right.  I clicked it.



Dragon's hand settled on the top of my head.  She ran it over my hair, using one finger to hook a strand and move it out of my face.  She did the same for another strand.



``What are you doing?'' she asked.



I opened his file, and I clicked through the tabs until I saw a map.



I tapped my phone against the screen.



There was a rumble outside, followed by a thrum, and movement beyond this craft.  Dragon had deployed at least two of the other suits.



``I need some communication here, Weaver,'' Dragon said.



Dumbly, I tapped the phone against the screen once again, not making eye contact.



``Please,'' she said, but she made it sound like an order.



\emph{What do you want?}  I thought.  \emph{Pantomime?  Do you want me to draw Teacher and the rest with my bugs and enact a play?}



I didn't do either.  I reached up and pulled off my mask.  I met Dragon's eyes.



I could see myself through the teleporter's vision.  Strands of my hair had fallen across my face as I'd removed the mask.  My lips were pressed together – I forced myself to relax them, only to find them resuming the position when I turned my attention elsewhere.  My body was all odd angles, my expression\ldots I didn't even know how to judge my own expression.  I didn't know my own face that well, all things considered.  It was only something I saw from time to time in the mirror, getting ready for the day.



Intense?  Focused?  Determined?



Fatalistic?  More crazy than less?



I held her gaze.



Again, I tapped the phone against the computer screen.



It chirped.  The data had been loaded onto it.



``If it was \emph{Skitter} that asked me, I would have said no,'' Dragon said.



I nodded.



``If I was convinced it was Weaver in there more than anything else, I'd feel a lot better about this.  Tell me, am I going to regret giving you this?'' she asked.



I couldn't answer.  Not even with a nod or a shake of the head.  I touched the screen again, going back a bit.  Region\ldots Chinese Union-Imperial.



C.U.I.



She knew what I was looking at.  ``I'm thinking of how we brought the Endbringers in, bullying people into helping, or at least getting them to stop \emph{hurting}.  Is this going to be a repeat?  Strongarming them?  Using your power?''



I shook my head.



My phone chirped again.



Others.  More targets.  The Birdcage.



Another chirp.



The rest I'd find on my own, provided all went according to plan.



I turned to the teleporter, then bowed low.  It wasn't because of her culture – she looked European – it was because a bow would have to serve as an apology, as much as a salute would have to serve as acknowledgement and thanks.



I met Dragon's eyes.



``I wish you could explain,'' she said.



\emph{I'm glad I can't}, I thought.  I turned to leave.



Glaistig Uaine was one hurdle I'd have to cross.  Dragon was another.



If everything went to plan, they were the biggest threats to me.  Scion excepted, of course.



I left the teleporter behind, making my way outside.  I turned on the flight pack.



My bugs sensed the teleporter making her exit, drawing a circle around herself and then promptly disappearing.  The Pendragon took off a moment later.



I approached my target.  The Simurgh was flying over a set of hills that would have been the Towers district of Brockton Bay, had we been on Earth Bet.  She was building something.



The fighting was ongoing, with Leviathan more hurt than alive.  Capes were fighting to get to safety rather than trying to hurt Scion.



Scion hit Leviathan, and the last buildings in the settlement toppled.



I turned away.  I wasn't one for prayer, but I wasn't really one for \emph{hope}, either.



At the same time, though, everything hinged on their ability to hold out.  Scion might leave soon, moving on to another target, but I wasn't so sure these guys would be able to hold out against one more attack.



I passed beside the Simurgh as I flew.  Checking.



\emph{No control.}



I plummeted.



The Simurgh, for the time being, came part and parcel with Tattletale.  When she wasn't fighting, she was a distance away from my teammate and friend.



I touched ground, then flew through the doorway at an upward angle, moving over the defensive line Marquis had set at the doorway.



I found myself back in Tattletale's company.  Marquis and Lung were close, but not so close they were in my range.  Panacea and Bonesaw, for their parts, were tending to the wounded.  The two girls froze as they fell inside my range.



Too many patients, on top of Panacea and Bonesaw.



Marquis and Tattletale froze as well, but it wasn't the same kind of freezing.  It was tension.



``No,'' Marquis said.



I ignored him.



``My daughter--''



Panacea stood up.  Bonesaw followed soon after.  They marched in Marquis' direction.



They passed out of my range.  Marquis draped an arm around his daughter's shoulders, hugging her closer.  Bonesaw wheeled on me, and there was a fury in her eyes.



It left only the wounded in my vicinity, along with a handful of others.  Members of the backline, the infrastructure elements in Gimel.



``Taylor--'' Tattletale said.



I ignored her too.



``I'm sort of getting what you're doing.  I don't get \emph{why}, but I think I get what you're about to do.  Don't.''



I closed my eyes, concentrating.  I needed to figure this out before I made any moves, or I'd be putting myself in danger.  Problem was\ldots there was so \emph{much}.



``Taylor, if you go ahead with this, and people start to catch on, you become public enemy number two.''



``Catch on?'' Marquis asked.



Tattletale didn't answer him.



I was pretty sure I had it.



With my power, I seized control of Doormaker and the Clairvoyant.  The pair stood, holding hands.



A heartbeat later, a cage of bone erupted from the ground.  Bindings wound around my legs.



\emph{He laid a trap under the surface of the ground}, I thought.



Some of the more mobile injured were backing away from me and my two hostages.  The remainder were still in my range.



Bone coffins encased each of them, sealing them to the ground, out of sight.



I paused, doing my best to get a sense of them.  I could get the gist of their abilities, focus to try and piece together the details.  There were a few capes who could have broken free, a few who were probably capable of slipping out one way or another.



But I didn't need to go that far.



I exerted Doormaker's power, and he opened a portal behind Marquis.  The other side of that portal was just behind me.



Memories hit me.  Being chained to the interrogation chamber, opposite Director Tagg.



Tempered confidence, even now?



The memories were distorted, moving just a little too quickly towards the end of \emph{that} particular scenario.  Except I was looking an awful lot like the person on the receiving end of the abrupt, painful and unexpected murdering.



Marquis' lieutenants approached.  Cinderhands, Spruce, one other I couldn't name, in dark clothes and chains.  Lung was circling around, getting ready to fling a fireball.



I used Marquis' power to block their paths with spiked barriers of bone.  When Lung, Spruce and Cinderhands \emph{all} tore through the barriers, with claw, some sort of disintegration power and flame, respectively, I used Doormaker's power again.  This time, the portals I opened were only about a foot by a foot across.  Four at once.



``Taylor,'' Tattletale said.  ``You're putting me in a pretty shitty spot, here.''



I checked my phone, tabbing through the pages that had been loaded onto it.  There was a blip marking Teacher's location.



More were gathering around me.  I made more doors.  One or two dodged out of the way.  I managed to catch them, anyways.



``I'm not getting enough details here to paint a picture.  I trust the hell out of you, but I'm not sure this \emph{is} you, Taylor.''



I pocketed my phone, then reached into my belt.  I hesitated for an instant, then pressed my hand to my chest for long seconds.  I knew I didn't have time to spare, but\ldots  no.  I didn't have time to spare.



I opened a portal twenty feet above Tattletale, then opened my hand.  The little tube of pepper spray dropped through the portal.  Tattletale caught it.



``You couldn't have made it easy?''  Tattletale asked, looking down at it.  ``Because standing by while you do this\ldots that's fucking \emph{hard}.  It's honestly easier if I'm on \emph{their} side and I'm helping them stop you.  If I can blame the fuck-up job Panacea did to your head.''



I didn't have a response to that.  I used Marquis' power to withdraw the bone cage and free my own legs.



I opened a doorway and passed through.



Dragon might be my enemy the moment she got filled in on what I was doing, but she was someone I cared about.  Teacher had fucked with her.



This next bit was going to be easier.





