





I made my way into Brockton Bay, the Boardwalk.  Five more steps carried me into New Delhi.  Only a minute later, I was walking through Brockton Bay again, downtown this time.



Los Angeles.



Bucharest.



Brockton Bay again.



Madison, Wisconsin.



Cauldron's Headquarters.



Ruins.  Places built up by man, painstaking, sometimes over \emph{centuries}.  Layer upon layer of human experience, history, and art, represented in stone and wood and glass.  Every single building had been put together with the idea of meeting some specific goal, a specific individual's tastes, filling a purpose as an institution, or being built to cater to society's tastes as a whole.  Virtually every building had been a familiar place to \emph{someone}, a home, a place of business.  Roads had once been a part of people's daily routines, bridges a convenience that was appreciated, if rarely acknowledged.



Shattered, eroded, dashed aside.  Roads were now uneven slabs, rising and falling, while buildings had folded or leaned over, spilling out their innards.  Those same innards hinted at just how much value we'd put into this world we'd built around ourselves.



I realized I'd stopped walking, struck by what I was looking at.  There was a tightness in my chest, and I struggled to put my finger on what to call it.  It was a sweet feeling, but not a pleasant one.  Not nostalgia, but it called to a certain kind of familiarity.



\emph{Home}, I thought.  \emph{This is home.}  Not so much a place I could return to for a hug, to kick my shoes off and let down my guard, not a place where I would sleep and wake up feeling warm.  Yet it was a place which was central to me, a place I was rooted in, and vice versa.



I'd defined myself in places like these.  The height of my growth, my strongest moments, they'd taken place in open graveyards and the aftermath of tragedies.  Not my best moments, not the noblest, but the moments where I'd had the greatest impacts and had made the choices that shaped who I was.



I started walking again.  I wasn't actually traveling to Brockton Bay, to Bucharest or Los Angeles.  I \emph{could have}, but I wasn't.  It was only that the ruins here were so easy to relate to those places, to this \emph{home}.  The memories of the locations were bleeding into my awareness, making it feel almost real.



I wanted to tell myself it was the clairvoyant in my range, but I couldn't quite bring myself to.  I wanted to say it was the distraction of having to devote a small share of my attention to ensuring that Doormaker kept opening portals when the clairvoyant recognized someone asking for one.



With a note of desperation, I told myself it was because I was still trying to keep tabs on my power, gauge my level of control, and manage my body.  If I couldn't get a better grip on my own movements, maybe I could get control over my swarm.  Over the people I was controlling.



But I didn't really believe it.  I was \emph{slipping}.



My bugs spilled out over the ruins.  My range was shorter, but I could use the relay bugs I had on hand.



\emph{Slipping}, the thought came back to me.



Losing my mind, losing grip on things.



The Faerie Queen had told me I needed to anchor myself.  Except I'd been doing that for a long time.  It was how I functioned.  Compartmentalizing, identifying a priority, devoting myself to it.  Surviving the bullying, the mission to turn in the Undersiders, the mission to save Dinah, to turn the city around, to save the world.  I'd had tunnel vision at the best of times, and I'd had both successes and failures.



I functioned best when I had a mission, something beyond the one singular goal before me.  Yes, stopping Scion was key, but-



I shook my head.  I'd stopped walking again.  Had to focus.



I'd use smaller anchors here, smaller things to tie myself down to reality, focusing on my surroundings.  If and when the time came, I would abandon them, cast them away in order of size and priority.  In a way, it would let me gauge how badly I was slipping.



An exercise of Doormaker's power let me experiment with the portals.  They couldn't move or drift, excepting the way they were anchored to the rotation of the planet as a whole.  Instead, I opened and closed new portals, timing it so the opening of one was a fraction of a second before the prior one closed.  I surrounded myself with them, a shifting, shuttering array of portals.



I was put in mind of the moment I donned my costume, of being Skitter the Warlord, with her half-cape, half-shawl.  There had been a kind of power to the gesture, to draping myself in the cloth and assuming the title and the role.



As I made my way through New York, I found myself altering the portals, reconfiguring them.  I'd drape myself in them like I did in a costume.



They formed a loose three-quarter circle around me, Doormaker and the clairvoyant, at first, a cylinder with an opening in front of me.  When I turned my head, they reconfigured, the portals in my way disappearing, replaced by others.



To streamline the portal creation, I layered them.  Two half-circles, overlapping.



And then, because it was the most compact way to fit the portals together, because I needed to make a \emph{signature, } to make this \emph{mine} and to make it \emph{me}, I made them hexagons.  A honeycomb interlocking of small, one-foot-diameter doorways, opening up to random points throughout the city, extending my range further than even my bugs could manage.  Each one showed a different image when looked through, a wall, a section of overcast sky, a bit of pavement.  It didn't stand out, serving more as a kind of camouflage.



As I experimented, finding the places to set the portals, my awareness of the city expanded in turn.



I sensed some of Teacher's squads.  Groups of men and women, always with at least one person who was more fit than the rest, all dressed in white, or at least in white shirts with jeans.  Most had backpacks, and all had weapons.  They patrolled, scouting the area, talking amongst each other in low voices.



Always talking about business.



I found Teacher.  He had a project in the works, and his `students' were busy scavenging.  A different sort of control than I had, with my bugs or the people in my sway.  More \emph{human}, maybe.  A society, rather than an army of troops gathered in formations.



The vast majority were active, each with a job to do, a task.  Men carried metal and electronics and either broke down materials or shaped them.  Women, just a little weaker in terms of physical strength, carried things like wire and baskets of clothing they had looted from stores.  Children handled the finer work, etching designs into metal and stitching.



I could almost respect it.  Except his motives were clearly selfish.



``Better to be fast than perfect,'' he was saying.  He paused to touch one of his subjects for a few seconds.  The girl stood there, eyes closed, while Teacher resumed talking, ``Follow the blue prints, or use the hub stations to get a clear mental picture.''



There were nods from the group around him.



Hub stations.  Not everyone was active.  There were clusters of two or three individuals that were each together, but I was pretty sure they weren't what he was referring to.  There were also some individuals that seemed to be operating as rally points for the others, arranged in a loose ring around their work in progress.  I watched one individual bring a car door to the rally point, touch the man in the center, and then make their way over to teacher.  He murmured, ``Metal and fiberglass design.''



Teacher touched him for four seconds, and then the man with the door made his way to a table, dropping a backpack and collecting a small crowbar.  As he started working, another man at the table stretched, grabbed a backpack, then joined one of the scavenging groups.



It was like a barn raising, but they were working purely in steel and electronics. Individuals that were tired switched to a different job, and everyone worked tirelessly.



They were building a Dragon-craft from scratch.



Not only a Dragon-craft.



``Eight costumes,'' Teacher said.  He approached a table, lifting one costume off the surface to investigate.  ``Not so flashy.  We want to fly under the radar.  Make it substandard, if anything.  C-list material.''



There were nods all around.  Teacher walked over to another table, lined with tinker weaponry and other tools.  His students were loyal, but they weren't \emph{puppets}, like mine were.  Their movements were natural.  The overall \emph{system}, though, wasn't natural at all.



I was put in mind of Regent's games.  There was the base of operations, the cluster of villagers managing the city, and there were the more independent squads of people, deployed to the world beyond the base camp, patrolling for enemies, ready at a moment's notice to be gathered together in a massed attack.



No doubt they were organized by ability.  Teacher could grant thinker and tinker powers.  If I assumed at least one tinker per group, with the tinkers carrying some ranged weapon or defense, and if the athletic members of the roaming squads were the soldiers, gifted with some knowledge that would give them a small edge in a fight, there were still two or three members in a given group I couldn't identify.



I wasn't even finished the thought when one of them perked up, startled.  She shouted, ``Scatter!''



Her group moved in different directions.



Trouble?



\emph{I }was the trouble.  \emph{It's a fucking precog.}



I opened portals, catching her three teammates, one by one.



It took two tries to catch her.  She was a fast runner, and she saw where I was putting down my portal before I'd even started, turning a hundred and eighty degrees around and scrambling in the opposite direction.



They were eerily calm, all things considered, much like Doormaker and the clairvoyant.  It made things easier for me.  But I knew that `easy' wouldn't last.



Teacher achieved control over people by giving them parahuman abilities.  The organization was important, and everything was key.  I'd moved too fast, and now Teacher's human systems were starting to kick into effect.



Men and women in an isolated cluster dropped to their knees.



``Amber district, team B-six,'' one of the students in the group reported.  His voice was as clear as a bell in the near-silence of Teacher's base of operations.  There were only the sounds of tools and the steady percussion of hammers striking metal, all in unison.



``What's the problem?''  Teacher asked.



``Out of action.''



``Change focus.  All observation teams, identify our target,'' Teacher said.



Heads in every second group around the base turned.  They looked my way, as if they could see the full five or six city blocks and see me standing in the middle of the road.



One crossed to another group, touching a young man.



``Weaver,'' the young man said, in turn.



\emph{It's like a computer.  Every person carries out a specific operation, and they're gathered in clusters with people who can communicate those ideas to others in efficient ways}.



``Tinker group H,'' Teacher said.  ``Defensive measures, modify them for micro-scale drones.  Forcefields, area attacks.  Group N, to me.  We'll need more tinkers on this problem.  We'll also need to this area.  Groups F and J, I'll recalibrate, put you on more general anti-clairvoyance duty.  She's- You're looking in, aren't you, Weaver?''



I reached out to place a portal in Teacher's camp, right behind him.  I hit a barrier, a dead zone I couldn't affect.



Some tinker device was blocking my clairvoyant, which was blocking Doormaker in turn.



My relay bugs didn't work either.  They only worked on bugs.



I began laying down portals around the perimeter, instead, finding the exact point I could affect.  The portals right next to me were turned around, so none faced me directly.  It wouldn't do if he had students open fire and shoot through the portal to hit me point blank.



``This is new,'' Teacher said.  ``Have I done something to earn your attention?  Crossed a line, somehow, maybe I inadvertently borrowed someone you care about?  I assure you, I'm very benign.  The \emph{vast} majority of my students here volunteered their services.  I told them I could use them to help stop Scion and save the world, and they agreed.  A number of others took the deal with the oath that I could borrow them for a year, and I'd supply them powers with no strings attached for the extent of their lives, no mental bondage at all.''



I frowned, shifting my weight from foot to foot, trying to ensure I didn't lose touch with my body.  If I had to move, I wanted to be able to move fast.



One of the groups was close enough to the perimeter of Teacher's base to fall in range of my portal.  I seized them, then took a second to analyze their capabilities.  Hyper-acute senses, enhanced aim, the ability to see through walls and a danger sense.



I thought of Tattletale, boasting to Coil in the moments before I'd pulled the trigger.



\emph{Not,} I reminded myself, \emph{that I'm pulling any triggers here.}



But I needed to disturb things, shake up Teacher's elegantly balanced operation.



They looked at one another, and I gauged the equipment they held.  The one with enhanced aim was the `soldier' of the group, armed with an ordinary gun and a bandolier of grenades.



I controlled his movements, directing him to grab a grenade from the bandolier.  He handed it over to the one with enhanced senses.



The one with the grenade raised his hand, hollering, leaning back, ready to throw-



My danger-detector reacted, and I had Doormaker create a portal, moving the grenade out of the line of fire.  A fat blob of crackling energy soared through the vacated space.



``You're full of surprises today,'' Teacher said.  ``I'm going to assume this is actually you, Weaver, and that you're not an Ingenue thrall or something similar.  I want you to know I'm not your enemy.  I was there for that whole business against the Elite, pitting Endbringers on them, I understand \emph{why} you did it.  You have your mission, a noble task, and you see it as a \emph{universal }task.  One everyone should inspire towards.  Peace and prosperity in your territory, because peace and prosperity are good things, am I right?  Please feel free to comment, strike up a conversation here.''



He gestured, and his crowd of students collectively backed away from the squad of students I'd taken over at one corner of his setup.  They faced down the others, their heads and shoulders visible above a section of wall that had fallen to the road hours ago.  I watched his group move, and tried Doormaker's power again.  The borders were at the same points.



``No?  Okay.  You'll have to trust me when I say I'm working towards the same end mission you are.  I want to stop Scion.  But I'm not a warrior, and I'd be offering more trouble than help if I was on the battlefield.  My students are fine when I'm giving the orders, but they're prone to undecision at key junctions.  I know where I need to be, I'll be there shortly, and I'll be of far more use to our side then.''



If the group had moved and the borders were at the same point, then it wasn't a \emph{person }generating the effect.



I used my bugs and Doormaker's power to get a sense of where the perimeter of this clairvoyance-blocking power was.  It was just a little irregularly shaped, but I could factor buildings and intervening obstacles into the area.  If there was a generated signal, it didn't extend as far with solid objects in the way.



``For the books, I was inviting you to ask where it is I was planning on going.  You seem more keen on silence.''



My squad turned a gun on the very center point, opening fire with a trio of bullets.



A box, a tinker-made device, exploded in sparks, popping into the air and bouncing off of the pavement.



I tested the clairvoyant's power.  It worked.



I placed portals with care.  Not to ensnare Teacher's students, but to cut them off.  Portals between them, above and behind them, in front.  Assuming twelve to thirteen feet of range, I could space them out and cover a wide area.



When I started tagging the groups, I worked from the outside in.  His precogs weren't amazing, with only a few seconds of awareness before their power gave them a heads up, but the trap was already in place.



I left Teacher for last.  No students at his disposal.  I made a portal, and then stepped through.  My soldiers aimed guns at him, while others stood stock still.



Teacher said something in a language I didn't understand.



I shook my head.  I didn't have a better way of showing my lack of understanding.



``No?'' he asked, smiling a little.



I shook my head once more.



``A shame, that,'' he said.  He sounded genuinely bothered.



My bugs flowed over him and through his pockets.  I didn't have silk, so I used thread from one of the workbenches, encircling the gun beneath his unfashionable corduroy jacket.  It wasn't a fast process, but Teacher saw what I was doing and helped it along, raising his hands to his head, simultaneously lifting his jacket up and away from the weapon.



I passed the thread to one of my new underlings, and they pulled the gun free.



My new minions began examining the gathered components and gear.  I looked through their eyes, taking it all in.



``I'm not \emph{unfamiliar} with robbery,'' Teacher said.  ``Parcel and part of this whole enterprise.  But this isn't you, I don't think.  For one thing, I'm working towards stopping Scion, in a roundabout way.  Or mollifying the damage he does, if stopping him isn't likely.  It seems things have turned around, then, if you're closer to being the Elite you were so recently condemning, and I'm someone working towards a fix.''



I gave him a hard look.  He shrugged, his hands still on his head, then said something in another language, smiling a little.



A code word?  A trap or trigger for some tinker device hereabouts?



Except nothing had happened.



``Well then,'' he said.  ``Scratch that.''



\emph{He tried something and it didn't work?  }My swarm shifted their stances, approaching a little closer, guns raised.



``\emph{Definitely} scratch that,'' he said.  ``Well then, I won't ask for your forgiveness, but I can still be blunt.  You seem different, and not so much for the better.''



My attention was on the tables.  Weapons, tinker gear\ldots I started browsing through it myself, joining the minions who weren't actively keeping Teacher at gunpoint.



``Can I ask \emph{why}?  Or is that too personal?  I understand second triggers can be mortifying.''



I turned around to face him.  I put my hand flat against my mouth.



``Mute.  I see.  And you came to me for help with that?  Do you want to be able to communicate again?''



I shook my head.



``Then you're looking to refine this ability of yours.  I can do that.  Give capes control over abilities that feel a little lacking in areas.''



Again, I shook my head.



``What did you come for, then?''



I didn't respond, my attention on the group.



I found what I was looking for.



Boxes, small, with a single, broad button along one side.  Like detonators.  There was nothing to them but a single LED, green, and a few ports where they could be plugged into certain ports or outlets.



I gathered them, tucking them into spare pouches.



``I don't suppose you could sock one for me?''



I shook my head.  I gathered all of them.



Then I began gathering the guns.



``This is inconvenient, for the books.''



\emph{You don't need these against Scion}.



``Again, my power \emph{is} available, if you should need it.  Anything that helps against our reciprocal enemy, you understand.''



He had an annoying habit of picking difficult-sounding words and using them instead of simpler options.  Like someone trying to sound smarter than they were.



I approached Teacher.  I saw him startle a little at the sudden movement.



He had nowhere to run, and he knew it.  He looked around, and he could see his own students caught in my snare.



I saw the surrender in his body language, an instant before he fell inside my power's range.



Memories hit me. \emph{ Announcing myself as Weaver in front of the PRT building}.  \emph{Taking on the role in New Delhi, coordinating two teams}.



I could sense his power, and I could sense his general awareness of the people he'd affected.  There was no constant connection between him and them, nothing like I had over my bugs or my subjects.



I moved another over to him, and I used his power on them.



There was a connection \emph{then}.  It only took a little bit of time, and focus on Teacher's part.  I could sense both the power taking hold, and the \emph{frailty}, the weak point that manifested at the same time.  There was a duality.



I let go of the subject, and I could feel that frail point linger, decaying by the smallest fraction with every passing moment.  \emph{That} was what Teacher sensed, an awareness of both the power and the degree of influence he had over the subject.



\emph{No, }I thought.  \emph{Not an option}.



I withdrew my phone, unlocked it, and found the page I needed.  I threw it to Teacher.  Rather than try to catch it with his clumsier movements, I had him grab the bottom of his sweater and lift it up, forming a net.  It landed in the `net', and Teacher collected it.



I backed away, releasing him.



Teacher staggered a little, then muttered what must have been a swear word in that other language.



``Karma, I suppose,'' he said, panting a little.  ``A\ldots little nerve wracking there.  I can't help but notice you didn't pursue with yourself, while you had me in command.''



There would be no way to use the power without leaving myself open to Teacher's influence.  No, I wouldn't be able to get myself a voice this way.  Not if it affected my ability to make decisions.  Not if it left a lingering window open.



These people who'd taken his promise of a lifetime of power, no strings attached, had been misled.



``Nothing, then?'' he asked.



I shook my head.



``A disappointment.''



I wasn't \emph{that} disappointed.  I had what I needed.  A speed bump for Scion, weapons, a little more information on how my power worked, and\ldots  I pointed at the phone I'd given him.  He glanced down.



``The C.I.U.,'' Teacher said.



I responded with a short nod, then held up one of the devices I'd collected.  I was picking and choosing the members of Teacher's collection I could use, arming them with tinker weaponry and gathering them near me.  I didn't enclose them in my little cloak of portals.



``Ah\ldots you guessed?''



I nodded, once.



``Understand, it wasn't spiteful on my part,'' Teacher said.  He lapsed into the other language for one moment, ``\ldots{}I gave them the switch in the hopes it would stop the incursions and curb honestly.  They were supposed to lock themselves away, but they held on to it, apparently intending to use it if anyone retaliated.  An ingress, a portcullis, if you will.  A way to raise the drawbridge and prevent passage into their castle.''



At my order, some of his students gestured with their guns, prompting him.



He seemed to take the threat in stride.  ``The one with a white button.''



I glanced at the ones in my possession.  I found it in a belt pouch and repositioned it.



``Skeleton key, Weaver.  I could make you force me to give up any of this detail, but I won't.  I want to get back to work, so I can \emph{help}.''



He was giving me a funny look, trying to drive home his point.



But this was a roundabout plan, some kind of infiltration, and he was clearly working \emph{against} our side.  I wasn't sure I bought it.



It didn't matter.



I gestured to the phone.  He moved to throw it back, and I raised a hand.  I pointed to my left.



He wasn't stupid.  He got my meaning, then used the phone to find the page I was referring to.



``I assume you're not looking to find \emph{me, }which leaves only the Birdcage.  No.  I haven't provided any devices to the Birdcage, or anyone alleged with it.  But you're going to find entering is difficult, regardless.  There \emph{are} security placements in measure.''



I nodded.  My soldiers got in place, rank and file around me, all armed.



``If I grasp your intentions, Weaver, I can speculate you'll be back for me later?''



I didn't respond.  No need to telegraph my plans to Teacher.  Still, the thinkers were figuring out what I was up to.



I was running out of time.



Which meant taking a leap of faith.



Using the clairvoyant directly was a dangerous prospect.  He could grant the power to see the entire world, multiple worlds, but \emph{breaking }that contact was troubling, debilitating.  I could see the toll it had already taken on Doormaker.



But I couldn't afford to hold back.



I separated Doormaker from his partner.  I could sense the effect, the sensory shift, the break in perspective, the mild nausea.  But he was functionally blind and deaf, and there were only so many senses that he had which could suffer.



I'd suffer far, far more.  If I made contact with the clairvoyant and was forced to break it\ldots that would be it.  Chances were good I wouldn't be able to carry on.  Things would be over before I recovered.



I took stock.  I had a squadron, now.  People who would have been slaves anyways.  People with simple abilities that were easy to get a handle on and use.  I had weapons, better than a typical gun.



Hopefully we wouldn't have to use them.



I took hold of Doormaker's hand, and I moved it to my belt, hooking his fingers through it.  Then I used my hand to take hold of the clairvoyant's.



My awareness started to unfold.  A slow, steady, gradual process.  I was aware of vast tracts of land.  I could see the damage done to Earth Bet.  It disoriented me, to see how we were in Washington, not New York.  Teacher had returned home.  Why had I thought we were in New York?



If I'd been distant from myself before, the enhanced vision made it that much worse.



I could remember how I'd once been \emph{comforted} by the fact that my power put the world in perspective, showing me just how small I was in the grand scheme of things.



This wasn't comforting at all.  Not this.  Not at this brutal\emph{ scale}.  I could sense the entirety of the world, from atmosphere to ocean floor.  I could, if I wanted to listen for it, hear the wind, the patter of rain, see the shimmers of heat on one side of the planet and the frost forming in caves on the other side of the planet, day and night at the same time.



\emph{I can see how the Doctor got a little detached from things, if she used this power with any regularity}.



Teacher said something.  I couldn't make it out, because I wasn't really listening.



I could see the other worlds and tally up the damage.  Not even a fifth of us were fighting, but those ten percent were giving it their all.  Others had retreated, finding family or friends to take shelter with.



I could count all of the individual collections of people.  Using Doormaker, the Doctor had scattered mankind over every available earth.  Collections of a few hundred to a few thousand.  People used to civilized life were starting over from scratch.  Makeshift shelters, fires, crafting tools.  They were tired, frustrated, and above all else, they were scared.  There was no news, no media, no way to follow the ongoing fight.



When I stopped looking, they didn't \emph{leave} my attention.  They carried on in my peripheral vision, as that field of vision continued to grow with every passing second.



The only real limitation was a set of blind spots, identical to the one that had hovered over Teacher's base of operations.  I could work around that.  There was also the fact that I could \emph{avoid }looking for things, and keep them out of sight.  I could avoid searching and seeking, avoid bringing something or someone into my field of vision.



Another anchor, another thing to tie me to reality, tie me to \emph{Taylor}.



I could see one cabin, off in the distance in Earth Gimel.  It would be three days of walking on foot to get there from the settlement.



Grue's cabin.



\emph{I'm so weak, }I thought.



I didn't want to look inside and see him with Cozen.  I didn't want to see them curled up in front of a fire, knowing the world could end at any moment, should Scion decide to shatter the landmass.



Instead, I fixed that cabin's location in mind, and I watched it from a distance.



I found my house, or what little was left of it, in shattered Brockton Bay.



I found \emph{people}.  I found Charlotte and Forrest.  I found Sierra, being very authoritarian and intimidating as she ordered refugees around.  She gave off an oddly familiar impression.



I found Tattletale.  She'd left her laptop aside and was helping with the wounded, talking with Rachel and Panacea in an intense, low voice.



Imp was giving somebody CPR.  Unlike the movies, most CPR attempts weren't successful.  Her patient was probably dead already, but she kept trying.  Ages ago, Grue hadn't been able to get her to take the first aid class.



Parian and Foil were moving around the outskirts of the battlefield, riding a stuffed animal.  Foil wasn't shooting, and it wasn't due to a lack of ammunition.



All the people I cared about, the things I wanted to hold on to, no matter what.



I found my mom's grave.  It was a part of the ruined landscape, and the earth had cracked open.  I could see the insect life surrounding the site.  Experimentally, I opened a portal.  My relay bugs passed through, and I cleared up the area, bringing the bugs to me.



Vanity, stupidity, but I felt a little better.  The area was cleaner.  Still in ruins, but cleaner.



And my dad\ldots



I hesitated.



\emph{I've lost so much}, I thought.  \emph{Forgive me, dad.  I need to have the hope you're still alive more than I need to know either way.}



I exhaled slowly.



Little anchors, more things to tie me down to reality.  I double checked the others were in place.  The least important of all, the mantle, the \emph{costume}, for lack of a better word, with the honeycombed portals, it was secure.  I had my goal, I had my mission.



I was still \emph{me}.  I was managing.



I turned my attention to Scion.  Apparently Tattletale had been right.  A bit of a fib on Cauldron's part, that they couldn't use the clairvoyant on him.  They'd wanted to avoid Scion finding them, avoid having him find his way to their laboratories.



When I looked, I saw him screaming.



Even for someone who had only ever spoken twice, it was an eerie, unsettling sound.  Raw, like he was being actively tortured, a sound of pain and anger distilled, given volume by his power.



He wasn't being tortured, though.  He was winning, tearing into the crowd with more ferocity than before, that same crowd where the others, people I cared about, were-



``Pose?'' Teacher asked, interrupting my thoughts.  I'd missed the beginning of what he'd said.



I raised my head.  It was more like I saw the movement of my head through a telescope than it was like owning the head itself.



Right.  I'd zoned out again.  Taking in too much.



Needed to move.



I was omniscient.  More accurately, I was as close to omniscient as I could hope to get.  It came with an Achilles heel, but I'd make do.



My phone had the last known location of the C.U.I. portal.  I opened a door to it.



I left Teacher behind.  He didn't warrant a goodbye.  If there \emph{was} such a thing as Karma, he'd get it soon enough.  For now, I would put off getting revenge for what he'd done to Dragon.  He'd be inconvenienced by the loss of his soldiers and disruption of his base of operations, but he'd recover.



Twenty parahumans flanked me as I walked down the dirt road.  I stopped when we'd come to the portal's location.  The C.U.I. had invaded, killing the refugees on the other side, then moved in.



The clairvoyant, moving at my bidding, took hold of the device I'd fastened onto my belt.



He hit the white button.



Teacher had sealed himself off in one world, to build up his students and work with Dragon.  He'd given that technology to the C.U.I., and they'd used it to secure their position.



Now I was breaking in.



The blind spot fractured, then dissolved.  I could see the C.U.I.'s empire.  Three hundred million people, many still migrating to places where they could settle, physically walking to separate themselves from others, so Scion couldn't kill too many at once.  I could see where Scion had attacked at one point, and they were still performing disaster relief.



There was a member of the C.U.I. who was officially known as Ziggurat, though she was really `T\textoverline{o}ng L\'{i}ng T\v{a}' to her allies and countrymen.  She'd used her power to erect stone walls and start the construction of a palace for the Imperial family.  Three walls stretched between three impressive towers, with the palace at the center of the \emph{acres} of empty space within.



I could see the Y\`{a}ngb\v{a}n in full force.  Three groups of sixty to one hundred and thirty capes, arranged on broad, square platforms of stone that had been raised off of the ground, each facing outward, their backs to the palace. Every one of them was in a matching outfit, their masks white, purple, and yellow, in turn.  They were tending to wounds, and the gaps in their number suggested they'd taken heavy losses.



Inside the place itself was a kaleidoscope.  Each room was mirrored several times over, the occupants moving in unison.  The main chambers had \emph{nine} iterations, each with a copy of the imperial family, each with a fourth squad of Y\`{a}ngb\v{a}n ringing the group in concentric circles rather than in rows and columns.  This squad wore masks like the others, multifaceted gemstones large enough to cover their faces, but the gems were a jade green.  The bodyguards, thirty in all.  The scariest capes in their group.



A young man, fourteen, sat on the throne.  On either side, their chairs just low enough to the ground that their heads were beneath the young man's, were family members.  Too young to be his mother and father.  A very young child, a girl, sat on a mat at their feet.  His sister.  I'd seen pictures of the new emperor and his sister when their older brother had been killed along with the Simurgh's attack on flight BA178.



They were joined by others.  Sh\'{e}n Y\`{u} the strategist was a surprisingly young man, wearing a black robe that was as straight and narrow as he was.  He was focused on a small tablet computer.  Beside him was Ji\v{a}, the imperial family's tinker, and surely the individual who had set up the kaleidoscope effect, throwing off would-be assassins and intruders.  T\textoverline{o}ng L\'{i}ng T\v{a} was there as well, a very thin Chinese woman with a black robe and heavily painted face.



Just below the dais were three more Y\`{a}ngb\v{a}n members.  Null, One and Two.  The key components in their power structure, the ones who divided the powers, controlled the squads and gave them the strength to be effective, respectively.



If I acted, I'd be targeted.  We'd taken out one of their armies, an infiltration and raiding party with the Simurgh's attack, but there were four groups remaining.  One of the \emph{other} raiding parties was less biased towards infiltration and more towards \emph{movement}.  They were the cavalry, the blitzers, the ones capable of flight and teleportation.  In the wake of the raids, the first strikes our side had deployed against them had been viciously counterattacked.  Quite possibly Sh\'{e}n Y\`{u}'s work.  Any attempt to attack was met by equal and opposite counterattack, targeting the leaders of the offensive party.



Even with nigh-omniscience, even with my portals, I wasn't sure I wanted to gamble on this.  Overconfidence at this juncture would be ruinous.



Better to sunder their confidence, than let my own be too high.  They weren't anticipating an attack.



But two hundred parahumans and a set of elite capes focused on defense and counterattacks was ominous.



I tensed, all at once.  A stray attack on Scion's part flew through the air.  I closed Doormaker's portals in the area, and it wiped out a building, along with six people.



I raised the portal again, connecting Gimel to the makeshift hospital.



Tattletale muttered something under her breath.  Panacea said something I couldn't make out.



Two of my favorite people in the world, almost wiped out without a chance to even know it was coming.



I looked at each of these things I treasured, the things I valued.  My leveled `house' in Brockton Bay, the graveyard, my ex-employees, my teammates\ldots and I looked at Scion.



There was no right answer.  No perfect battle plan on this end.  There was no \emph{time}.



I exhaled slowly, forcing myself to relax.



Then I began opening portals across all of the different worlds I could reach.  I began gathering bugs en masse.



I'd heard once there were ten \emph{quintillion} bugs in my world.  Eighteen zeroes.  I couldn't control that many.  Or, to be precise, I couldn't afford the time to collect that many.



\emph{Fourteen} zeroes?  If I had a dozen worlds, each with really good swamps and rainforests to tap into, my relay bugs to help extend my pitiful, three-hundred foot range?  \emph{That} was doable.



Fuck it all.  There was a time for strategy, and there was a time for the brute force approach.  Hell, the brute force approach could be called a strategy unto itself.



I'd find out about Sh\'{e}n Y\`{u}'s power the hard way.  He could see attacks coming.  Did it work when the attack came from every direction?



I divided the bugs into tenths.  Then I opened nine portals into the Y\`{a}ngb\v{a}n's world.



The tenth I opened into Earth Bet, above the portal I'd reopened.



They \emph{did} react.  Sh\'{e}n Y\`{u} \emph{did} manage a nigh-instantaneous counterattack.  A hundred capes deployed to my general area, teleporting in, and then flying around with speeds that would have put them on par with cars on a highway.



I watched from a distant location as my hand clenched, squeezing the clairvoyant's.



But I'd deployed a tenth of the bugs on my location.  I was hidden within an impenetrable cloud of bugs.  I raised Doormaker's portals as shields around me.



Some entered the cloud, and the response was swift and brutal.  The bugs consumed them, and my minions with the tinker guns shot them.  I moved to a different world, closing the door behind me, just to make their job a little harder.



The other squadrons had their own means of defense.  One had eighty or so people burning red hot, torching the bugs by heating up the air.



I began using portals, and I captured the group.



``If you little fucks had any sense, you'd know that getting the upper hand on me, just for a moment?  It's something you should be \emph{fucking terrified of.''}



Not my voice in my head.



\emph{``Oh?  The ineffectual little girl with the bug costume is awake.''}



Memories of confusion, a pain unlike any other.  Of utter helplessness.



\emph{What would my mom think to see me now?  }A thought from a different moment than the others.



I used Doormaker's portals to capture other groups, though they were more scattered.



When I had the majority of them, I turned them against the palace.



Ziggurat closed up every window and door.  The ring of Y\`{a}ngb\v{a}n members was standing now, on alert.



It hardly mattered.  They'd amassed this much sheer power, they'd controlled the people through manipulation, and now they were seeing what happened when the people turned on them.



I felt a kind of anger swelling in my breast, and I knew it wasn't \emph{mine}.



But it was still a feeling I could ride.  Something that could carry me forwards.



Fuck them.  Fuck them for not cooperating.  Fuck it all, I shouldn't have had to go this far.



The attackers tore down one wall.  I saw one of the six mirror images of the kaleidoscope interior fade away.  The interior was heavily trapped, laced with poisons, rooms with only vacuum within and, ironically, poisonous bugs.  Had someone tried teleporting in, chances were good they would have met a grisly end.



I moved the attackers around the outside of the palace, rather than subject them to the traps.  They attacked different walls.



One wall was penetrated, and two more shares of the mirror image faded.



There was another contingent of Y\`{a}ngb\v{a}n within one of the revealed partitions.  Red masks, like the ones I'd seen in New Delhi.  A small squad of throwaways.



I controlled them too.



It wasn't long before the last mirror images fell.



My portals ensnared the remaining Y\`{a}ngb\v{a}n in a few moments.  The fighting stopped all at once.



I added Zero, One and Two to my swarm.



\emph{Alexandria, choking on bugs}.  They \emph{hated} me for my arrogance.  For what I was.



I exhaled slowly.  They were a little more aware than the others.



Two's power enhanced other powers.  Refracted throughout the Y\`{a}ngb\v{a}n, it was what allowed them to have sixty powers at one fifth of the strength instead of sixty at one sixtieth.



Her power worked on my own.  I felt my control clarify.



In front of me, One extended a hand, then carefully closed it.  I moved it experimentally, testing the range of motion.



Not as perfect as if it were my own hand, back when I had full control over it, but \emph{better}.



I wouldn't be sharing this one.  I couldn't afford to.



Sh\'{e}n Y\`{u} spoke.  It didn't sound Chinese, with the wrong cadence.  It was a question, by the sound of it, accusatory.



Maybe there was a power that would have made sense of it.  It didn't matter.



There were five layers of overlapping hexagons, now.



I had my army.



But it wouldn't be enough.



\emph{On to the Birdcage}, I thought.



I opened portals for my swarm to pass through.



I passed through, and I found myself in the midst of ruins.



Ruins, like I'd been thinking about before I met Teacher.



I used the clairvoyant's power to search my surroundings.



No.  The structure was only partially intact, devastated by Scion's fury, by shockwaves and literal waves.  That it still stood was a testament to how solid it had once been.



\emph{This isn't the Birdcage}.



\emph{Gardener}.  My old jail.



The disorientation rocked me.  To get my bearings, I didn't reach for more \emph{geographical} reference points, but I reached for the little anchors I'd formed instead.  I checked and double checked them until I could be sure I was stable.



For the second time, I tried to make my way to the Birdcage.



I stepped through the portal, moving myself to a peak above the Birdcage itself.  Though I couldn't really \emph{feel} it, I was aware of how cool the air was, the fact that my body, so small on that vast mountain, was sweating pretty heavily.



Being surrounded by thousands of billions of bugs had drained me more than I'd been aware.



Another weakness, another point where I'd disconnected just a bit too much.



Was my own body supposed to be an anchor?  Was that something I should cling to, at the expense of other things?



I made myself draw in a deep breath, until my chest hurt, and it still felt so paltry compared to the \emph{hundreds} of people I controlled.  The view, this majestic image of the landscape, of a sky that \emph{still} harbored the clouds of dust and debris from Scion's earlier attacks\ldots it was but one piece of a scene viewed from a hundred different pairs of eyes.  Virtually all of them had better vision than I did.  I was adrift in an ocean of input, one body, harder to control than all of the others, so easy to forget about.



I'd done it without thinking, bringing them with me.  They stood on ledges and jutting rocks all over the peak, surrounding me.  More than anything else, I could feel their fear.  With so many of them, it was indistinct.



I forced my own head to move, felt the crick in my neck, where I hadn't really moved my head in a long time.



The ones who were still in the Birdcage were the ones the cell block leaders had felt apprehensive about.  Not necessarily \emph{stronger}, but less predictable, less reliable.  More of a danger than a help, if given free reign.



As far as I could tell, it was the last large group of experienced capes I could collect.



I opened a portal within the Birdcage, to capture my first prisoner.



Containment foam rained down from the ceiling, sealing him in place.



\emph{Dragon}, I thought.



I didn't make another move.  I waited.  I'd expected this.  It was why I'd come here in person.  I could use the clairvoyant's power and see a hangar in one mountain valley opening up.



It took only a minute.  A small armored suit arrived, a fast-moving model rather than a heavy combat model, much like the one she'd used to counteract our first attack on the Brockton Bay PRT headquarters.



It perched on a rock in front of me.



Dragon's weapons were primed and ready to fire, the threat implict.  When she spoke, her voice as clear as a bell in the clear mountain air.



It was the same language Sh\'{e}n Y\`{u} had spoken to me.  The same incomprehensible language Teacher had lapsed into.



\emph{English.}



When I met Dragon's eyes with my own, my \emph{head} shook with the shock I felt.  I might have collapsed, numb, if I hadn't been holding on to the clairvoyant, with Doormaker gripping my belt.



It was the anger that kept me going.  I'd felt a glimmer of it when attacking the palace.  I'd felt it when dealing with capes and civilians every \emph{damn} step of the way.  The only thing I wanted was for everyone to do what they were supposed to do.  To be good and to be fair, feed the hungry, give shelter, to fix the things that were broken and to fucking band together against the \emph{real} monsters.  Save the world.  For the world to make some damn \emph{sense}.



I found myself chuckling a little, and it was just as displaced and not-quite right as any of my individual movements.  Off kilter, more like I was doing a bad job of acting than real laughter.



I couldn't stop it, even as I tried to pull myself together.  I turned my face towards the sky, my eyes streaming.  Her voice continued, insistent, the gentleness giving way to concern.



Hardly the last injustice I'd have to face down in the coming hours, but it was a front runner for the biggest.  The most decent damn person I'd ever met, and she wasn't even human.  She was the only person who was definitely still alive who'd helped me without an iota of selfishness.



I couldn't negotiate my way out of this.  Even with the rapport we'd established, I couldn't trust her to give me the benefit of a doubt.



As much as I didn't want to, I knew that the only way forward would be to destroy her.





