





I didn't break eye contact with Dragon.  My eyes were damp, and it was impossible to find a balance in terms of keeping still.  I either slumped over or I held myself so rigid that I trembled, an ache creeping over my body, my muscles too taut.



Back when Emma and I had been friends, way back in middle school, we'd done one of the sleepover dares.  Going into a dimly lit room and staring out our reflections.  Repeat the name of the monstrous woman, a name that escaped me now, over and over, without breaking eye contact.



The freaky thing had been that it had worked.  My expression had torn, twisted and distorted, dark patches creeping over my cheeks and forehead, my mouth disappearing with only a blank stretch of skin in its place.  I'd fled the room.



I'd later read up on it, because understanding something meant being able to handle it, and my problems back then had been ones I could understand.  The effect was a result of the mind's idleness.  We only really saw a little bit of what we looked at, and our brain worked constantly to fill in the gaps and unimportant spaces with its best guesses.  In a dimly lit room, with the mind focused on the steady, hypnotic repetition, the brain would fill in spaces with the only reference points available to it, taking from features in its field of view to patch together the face.  Fear, imagination and the recently-told scary story of having one's entrails ripped out through their mouth did the rest.



The mind was an amazing thing, but it had limits and weaknesses.  I'd been taking in too much even before I added the clairvoyant.



Dragon spoke, her voice insistent, concerned, and pitched as a question at the end.



I raised my arm and the stump of a limb to the sides, bringing the clairvoyant's hand with me.  An exaggerated shrug.  I then let them flop down to my sides.



Dragon said something else in response, a statement, quiet.



Using the clairvoyant was an art, it seemed, and I hadn't received any advice on how to handle it.  I was figuring it out, though.  My focus on Dragon was like staring into the mirror.  There were too many details to clarify to keep my attention in one place for so long.  Things were starting to bleed around the edges in areas I wasn't focusing on, like a watercolor painting that was bleeding out beyond the lines.



Subtle, but it was there.  Was it the entity, trying to tap into my memories to hash things out where my perceptions were failing?  It wasn't anything substantial, not yet.  I was focused on Dragon, above all else.  The various people, the capes, the fighting, all were clear in my awareness.  It was the hills, the mountains, the vast spaces of water or field without anyone nearby that were shifting subtly.  Cities in particular seemed to be a jumble.  Or was it just easier to see the differences and errors when a city was rearranged in a way that didn't make sense?



More to the point, was I simply losing my mind entirely?



\emph{I'm running out of time.}



I raised my hand again, reaching out towards the Birdcage, below us, towards the comparative miles of space and containment foam, the forcefields and countless other effects that had been worked together to form the most secure facility they could manage.  The empty space between the hanging structure itself and the walls that had been thickened by the engine was vast in a way that staggered me, just a little.  Shit like that didn't help with the fucked-up perception thing.



My hand was shaking, the muscles in my forearm too tense, the hand too loose.



Without breaking that eye contact, I gestured, turning my hand over, curling the fingers.  I opened a portal at the same time, inside the Birdcage.



Dragon shifted her stance, and that same room flooded with containment foam.



She said something in that same, quiet voice.



As communication went, it would have to do.  Not the words I couldn't understand, but the gestures.  I'd declared what I wanted, she'd drawn the line.



I wanted so badly to hug her, to cross the distance between us and throw my arm around her muzzle, or around one of her legs.  To have something physical to hold on to that I wasn't actively controlling.  I couldn't give her an opening to take me out of action.



I began opening a portal beneath a flow of lava, a trickle on Earth Bet, at the mouth of a cave system.  The lava met the edge of the portal, and it winked out of existence.  A splash of it passed through the portal, touching Dragon where her `neck' met her body.



She moved, jet-engine `wings' reorienting, pulsing with thrusters going on full to move her fifty feet to the right.  Her claws met a cliff face, digging into stone, and the thrusters kept going, pushing her against the rock and holding her on the surface.



\emph{Right.  Okay.  A different tack then.}



She was retaliating, too.  Her guns trained on me, barrels glowing.



I opened defensive portals before I even saw what she was firing at me.  Lightning, crackling in visible arcs around what looked like sphere-shaped empty spaces.  Controlled pockets of ionized atmosphere, probably, to give the lightning a path to travel.



The lightning traveled through the portal and struck Scion from behind.  I closed the portal before he could react.



The guns changed, the barrels contracting, the mounts behind the barrels reconfiguring.  A portal simultaneously opened behind me.



She sprayed containment foam.  Not a stream, but an honest spray, as if she was trying to paint the entire mountain peak.



I stepped through a portal, putting myself halfway on the other side of the world.  I stood on the roof of the Byzantine Tower in Istanbul.  Third tallest building in the world, surrounded by a shattered city and waterways that were now polluted with detritus and rubble.



Then I opened fire.  Every parahuman I controlled with a ranged attack or gun fired into the portals I was opening beside them.  The exit-points were beside Dragon, and a cascade of bullets, lasers, energy shots, ice, lightning, metal and other effects obliterated her ship, tearing through the cliff face.



I moved my collection of people out of the way before the resulting rockslide could kill anyone.  The thinkers and tinkers joined me, the rest relocated to other points on the mountain.



The ship she'd sent my way was slag.  Barely worth calling scrap metal.  I checked it over twice.



Dragon deployed her drones.  Not ships, but tens of thousands of airborne craft, most no larger than a basketball, kept aloft by antigrav panels like the ones on my flight pack.  I already knew that each was loaded with a specific payload.  Containment foam, EMP pulses, explosives, tear gas and more.



This wasn't a typical fight.  It was more like a war, two parties with vast resources at their disposal, with armies and incredible potential in terms of the tools we could bring to bear.  In a typical fight, things would end when one person knocked the other out, but a war rarely ended that way.  The fighting would continue until we'd done enough damage to the other that they had to give up.  Dragon was decentralized, with no single point that could be attacked to remove her from the fight.  Truth was, I'd probably have to destroy everything to destroy her.  If she didn't give up.



If she \emph{could} give up.



As for me, I was inaccessible, out of reach.



I was quietly confident I could win this, one way or another.  She'd have to defeat every cape in my little army, every cape I potentially acquired in the meantime, and I doubted her willingness to do that.



\emph{Don't destroy my army.  Please don't be willing, don't be capable.  If that happens, then I've failed completely and totally, I've done this to myself and will go out as a villain, all for nothing.}



The fight against Scion was ongoing.  I needed to be able to focus, especially with the way things seemed to be breaking down in the least important areas.  I couldn't split my attention between him and Dragon, or something that was nigh-impossible would become harder.



The drones closed the distance, and my army began gunning them down.  They were evasive, and I could take in the whole picture to see how Dragon was managing them.  Not simultaneously, but close enough it barely mattered.



I tapped into precogs and clairvoyants, along with other thinkers, gauging the best approach.



Sh\'{e}n Y\`{u} informed me of the general thrust of Dragon's attack.  I could see it through his perceptions, mottled, indistinct lines in the battlefield.  X drones moving to one of my groups, Y drones to another.  The path they intended to travel\ldots I could tell that as well.  An initial wave of attacks to debilitate, and then the second wave, drones for a follow-up strike.  The lines had a feeling to them.  I could almost assign labels.  Infantry, cavalry.



I looked around me.  If I drew parallels, tried to correlate what I was seeing with what Sh\'{e}n Y\`{u} was seeing\ldots



She was aiming to strike me.  \emph{How}?



Seventeen Dragon-craft deployed from the hangar.  Again, not combat models, but utility models, fast response and rescue.  Craft she'd been holding in reserve, no doubt because the cost of deploying them outweighed their potential benefit against Scion.



The clearer Dragon's direction of attack became, the more Sh\'{e}n Y\`{u}'s awareness clarified on her weak points.  Distant locations and objectives.  Some were objectives I couldn't identify, even with the clairvoyant.  He only saw within the boundaries of Earth's atmosphere.



Others\ldots valid targets.  I sent one squad to an army base.  Pulses of gravity and intense heat let me detonate the contents of a munitions depot and direct the force of the explosion in one direction.  The end result annihilated a data center Dragon had set up nearby.



\emph{I'm sorry.}



I could see her reaction, in the broadest sense.  Where her drones had been micromanaged before, they weren't being controlled now.  She was focusing elsewhere, controlling the larger craft and assigning them to the protection of the various data centers.



There was a skeleton crew of people at one facility.  A data management firm that Dragon had bought out, I suspected, because the entire databank was reading as hers.  Row upon row of servers, standing like tombstones in refrigerated rooms.  Freezing air poured through the floor, pushing up against the warmer air.  The facility seemed more like an alien landscape of steel and cold than anything of human design, complete with a constant, persistent weather pattern – a constant, gale-force wind generated by the movements of hot and cold air in what had to have been a careful design.



That the crew had stayed suggested something about their personalities.  Discreet, paranoid people, who'd built a shelter inside the facility as a hiding place, in case things went to hell.



Which was pretty damn reasonable, considering the sheer amount of nightmarish crap there was in the world.



I used portals to take control of them.  I couldn't read what was on the screens, so I had them take a more direct route.  They made their way through the building, throwing switches, pulling plugs and opening sealed doors.



Three of my Y\`{a}ngb\v{a}n capes entered the facility through portals and began generating heat as they'd done outside the C.U.I.'s Imperial Palace.  I could find the freezer\ldots and another cape could step through to damage it.  Dragon's utility craft arrived on site, but the damage had been done.



\emph{I'm sorry}, I thought, again.  My attention shifted to the monitors and gauges in her various databanks.  I could see dials shift closer to red, numbers rising, gauges nearly filled.



Dragon could manage her things, I told myself.  She had safeguards, ways of keeping her data safe.  There was no doubt in my mind on that score.  Each time I disabled a facility, I forced her to consolidate, to put the resources that remained under further stress.



My ranged capes aimed for portals once again.  This time, I put the exit portals against Earth's atmosphere, aiming for the general direction of a satellite.



It took thirty seconds of sustained fire before Sh\'{e}n Y\`{u}'s power stopped telling me it was a weak point.  Other thinker powers in my range were giving me similar feedback.  A cape with perfect eyesight was telling me it could even see the explosion.



The displays across Dragon's private realm shifted further.



She was saying something to Defiant, words I couldn't make out.  I could see him tensing, moving like he was going to go somewhere.  Then Dragon spoke again, and he went still.  His head turned in Scion's general direction.



\emph{Please stop}, I thought.  \emph{Don't make me go further.}



She went further.  She intensified and organized the attack, and her drones reached my front line, disabling them with nonviolent means.  Tranquilizers, electric pulses, containment foam and tear gas.



I let it happen, because I needed to see what her second wave attack was, before she organized a more efficient frontline attack.



The second wave approached, and they made a beeline for the portals that were controlling my minions.  The portals that would exit right next to me.  But the drones were too large\ldots



Until they jettisoned outer shells and accelerated.  Half the payload, but they had the same kind of propulsion jets I had in my flight pack.  I moved the portals a fraction of a second before they speared through, and they continued onward through open air.



Sh\'{e}n Y\`{u} informed me about the third wave's imminent attack.  Not a feeling of attack, but\ldots the initial wave had read to his senses as something like infantry or spearmen.  The second wave had read as cavalry.



This?  A siege weapon?  The lines that Sh\'{e}n Y\`{u}'s power painted on the world indicated something deliberate, devastating, but diffuse, somehow indirect.



I directed fire at the drones, and forcefields served to protect most.  The non-Y\`{a}ngb\v{a}n capes I had that could penetrate the forcefields were few and far between, the drones too numerous.



They set up, planting their mechanical limbs firmly on the ground, and then they deployed, pyramid-shaped structures, glowing blue at the peak.



My portals began opening, ones I'd closed not long ago.  Portals I'd opened to control my capes, and the larger portal I'd opened to escape to this location on the Byzantine Tower.  I couldn't shut them.



Drones started to make their way through.



I, in turn, opened another portal, handing one tinker device to Sh\'{e}n Y\`{u} before hurrying on, leading the rest through.  Portals blocked the drone's ranged fire.



The Y\`{a}ngb\v{a}n's strategist used Teacher's device, and all the doors in his vicinity slammed shut.



Dragon's path to me was shut.



I watched the meters and gauges.  Each attack had pushed Dragon's remaining resources closer to capacity.  That was on top of the extra strain she was under with Scion having done so much damage to the Eastern seaboard.  He would have eliminated other databanks when he'd attacked.  Just like me, she'd been wounded and disabled before entering into our private war.  Just like me, she desperately wanted to focus on Scion, but she couldn't afford to.



If each attack pushed the remaining databanks four percent closer to capacity, at a guess\ldots no.  I was having trouble putting the numbers together.  Had to eyeball all of it.



I targeted another facility.  All of the ranged attacks, channeled through open portals, ripping through an unoccupied facility.



In quiet horror, I watched meters flip over into the red, gauges hitting maximum capacity, bars filling, characters on screens going nutso until they were all the same digit, repeated ad infinitum.



One by one, monitors went blank.  Server banks I hadn't even touched began to spin down, fans stopping, lights fading.  Whole grids of blinking green lights winked out, some in order, others at random.



I watched, silent and frozen, as the process continued.



\emph{Stop,} I thought.  \emph{That's enough.}



You have backup servers, I thought.  Those servers need to stay online.  They have to stay online, because you can't exist in stasis any more than I could.



She needed life support, at a bare minimum.  She couldn't go any length of time without something running any more than I could go for a duration without a heartbeat or breathing.



But the lights continued to go out.



She said things to others, over the comms systems.  To Chevalier and other various heroes.  A few words or a statement or two, specific to each of them.



Some longer words and phrases dedicated to Defiant, and more acerbic words for Teacher and Saint.



Saint didn't react, but Teacher raised his phone, tapping it a few times before saluting the air with the device.



The drones close enough to do so sank to the ground all across the mountain's peak.  Her suits had already retreated and settled on the ground.  Defiant was very still as he watched them land.



Then Scion attacked, screaming incoherently, and Defiant moved, taking control of one ship.



The last of Dragon's lights went out.



I stood in a daze as the various machines went still, surprisingly hot as the fans stopped spinning.  All of the server rooms and data banks were utterly dark and quiet.



Drones that hadn't been close enough to the surface to land dropped out of the air.  They hit the ground, along with one or two members of my swarm, and I flinched with the crashing, as if they were striking me.



\emph{I'm sorry}, I thought, but it wasn't my thought.  A memory.



It was good that my power was saying it, because I couldn't.  My own thoughts were a jumble.



My feelings were a chaotic mess.  A lump was growing in my throat, swelling beyond my ability to tolerate it.



I hunched over, and I very nearly let go of the clairvoyant's hand before remembering that I couldn't.  Instead, Doormaker and the clairvoyant both pulled at my mask until it was halfway up my face.  I felt the lump become a wave of vomit, spattering over the rooftop.  It hurt, not just the physical act, and yet it felt like so little.  Still a scene I was experiencing while half-numb, experiencing from a distance.



\emph{I miscalculated?}



Had she been vulnerable because of what Teacher had done to her?



Something else?



Did it even matter?



I felt the need to throw up again, almost wanted to, just for that relief from what was welling up inside.



She'd been an ally, a friend.



I wanted to scream, to yell at her for being like all of the others and refusing to play along, to listen and cooperate.  I wanted to do the opposite, to beg her forgiveness, and hate \emph{myself} for being exactly what I'd criticized others for.



I wanted to put all of those feelings aside and start dealing with Scion.  I wanted to give up on that entirely, because, fuck it, what was I even trying to save, at this point?



If I'd been whole, if I'd been balanced, I might have been able to find the middle road between the conflicting ideas.  But I wasn't.  I remained hunched over, almost paralyzed.



My anchors\ldots what had I chosen, again?  Tattletale, Rachel, Imp\ldots Grue's cabin.  My interlinking hexagonal portals were a mess.  In the course of fighting Dragon, I'd closed portals and opened others without any attention to keeping it together. That was something to pay attention to.  If I wasn't feeling my emotions as clearly as I should, I had to look for the external clues, and that jumble was suggestive of an emotional turmoil I'd been suppressing.



I began pulling the grid back together, not feeling any better.



\emph{What else?}



I reached out, trying to remind myself of the anchors I'd set up.



My mom\ldots I found the graveyard.



My old house\ldots



Where had it been again?



The streets were such a mess, one pile of rubble virtually indistinguishable from the rest.  What was I supposed to even do to identify it, if there were no landmarks?



I'd hoped to use the anchors to help push myself forward, but reaching for one thing that I'd known from the very beginning and failing in the process left me in a more unbalanced state.



\emph{I was\ldots}



\emph{I was what?}



There had been an idea I'd been reaching for, a word, a symbol, something.  Yet I couldn't clarify it in my head.



\emph{Don't panic}, I thought, but the words sounded panicked in my head.  Rushed.  Sloppy.  My breathing was hard and fast, my heartbeat pacing out of control.  Between the two, it was getting to my head, affecting my thoughts.



\emph{Don't panic}, I told myself.  The repetition felt good, helping.



Or had it been my passenger telling me not to panic?



\emph{No.  I had a perfectly normal lapse.  Perfectly normal.  A person in a stressful situation like this is going to have moments where she can't come up with the right word.}



\emph{Perfectly normal.}



My breath wheezed a little as I panted.



You don't want to, but you have to, I told myself.  Stop Scion.



The portal slid open.



Except I hadn't ordered it.



\emph{You want to take over, passenger?}  I thought.  I began to struggle to my feet.



The drones moved.



Defiant?



Saint, taking over her systems again?



They flowed through the doorway to Sh\'{e}n Y\`{u}, blitzing him in passing.



No.  Neither of the two seemed to be paying attention to me.  They were focused on Scion.



I began erecting portals, shooting the drones out of the air, defending myself against the initial bombardment of tear gas canisters and containment foam.  If I was slow to react, it was because of the disorientation, the lack of knowledge of who and what I was up against.



I had other thinkers available.  Understanding their power was easier with the Y\`{a}ngb\v{a}n's power boost.  If they were puppets, the power boost meant the puppets fit my hand.  I put them to work, trying to divine just who was seizing control of these drones.



It was so much easier to operate when I was \emph{doing} something.  Time and again, my lapses, the \emph{slippage}, it had been in the quiet moments, between the conversations and the fighting.



It was easier if I was active, in the midst of conflict.



This was me.  I thrived when I had an opponent, and when I could carry out that goal I'd had from the beginning, getting the world to the point where it all made \emph{sense}.  Bringing people in line, subjugating those who would get in the way or do more harm than good.



That was how I functioned.  I'd always reveled in the chaos, in the madness of it all.



\emph{No}, the thought crossed my mind.  \emph{Not always}.



Once upon a time, I'd been Taylor, minus the powers.  I'd avoided conflict.  I'd just been trying to get by.



\emph{Does that mean this is you, passenger?}



There was, of course, no reply.



The drones kept coming, and I redoubled my efforts, calling individuals to me to form a battle line.



The moment the line was in place, the drones shifted.  Some entered the portal, then immediately made a `u' turn, flowing back around the sides of the portal and down.  They circled around the building, trying to get at me from behind.  I had to redistribute my personal army to block them off.



The portals were open and I couldn't close them.  But the lights on the drones were off.  No lenses glowed, the antigrav panels were the only thing that indicated any power at all.  Remote control of some sort?



\emph{The lights are off, but they're still running}.



I laughed, abrupt, an alien sound, not my own laugh.



\emph{The goddamn lights are off!}



It wasn't Saint mounting this attack against me.  It wasn't Teacher, or Defiant, or any of those other guys.



I continued laughing.  My winded panting and nausea from before translated to a kind of lightheadedness.



Fucking \emph{Dragon}.



Fucking with my head.  Giving me a reality check.  Trying to catch me off guard.  She'd figured out that I had the ability to see her systems, she'd switched off the lights on the panels, put every system into hibernation, stopped the fans, and cut everything down to a bare minimum while the fans had stopped, so they didn't overheat too quickly.



A drone that had crept around behind the building detonated in a flare of pale sparks, and every portal in the vicinity distorted, taking on weird shapes, more three-dimensional than two-dimensional.  They winked out of existence.



Leaving me in the midst of an army I no longer controlled.



\emph{Fucking tinkers}, I thought.  But I was strangely overjoyed.  I was fucked over six ways from Sunday, but I was happy.  I \emph{hadn't} murdered one of my favorite people.



The capes at the edge of the rooftop were looking around in a daze.



The drones were moving, assuming a perimeter.  The capes at the edge of the rooftop looked lost and shell-shocked.



And I was still laughing, clutching the clairvoyant's hand as if it was one of the few things keeping me grounded.



Capes at the edges retreated, bumping into one another.



The laughter stopped as I abruptly let out a sound, half-roar, half-scream, incoherent, channeling every last iota of the lingering rage and despair into the noise.



I commanded the people in my range to attack the drones, and I continued screaming even as my throat began to hurt and I felt like I might pass out from oxygen.



Dragon was only just beginning to speak, some drones blaring out words in what might have been English, others in a sing-song dialect that was likely Chinese.  The percussion and detonations that followed the attacks striking home drowned out most of it.



The ones at the edge took cues, attacking the drones they'd just been fighting.



Each and every one of them had been brainwashed.  Some by Teacher, some by the Y\`{a}ngb\v{a}n. They hadn't had freedom of choice for some time.  Between the scream of rage, a pretty damn universal sound, and the action of the ones I \emph{did} control, they defaulted to going with the crowd.



I still had to deal with Dragon.  Her intent was clear, from the way the drones were moving.  She wanted to target \emph{me}, and stop me from the source.  I needed to do the same, and I needed to do it without destroying her infrastructure.  I wasn't going to risk making that faked death into a real one.



\emph{Fuck you for fucking with my head at a time like this}, \emph{Dragon.}



The thought wasn't one of malice.  My feelings were so confused I could barely tell on that front.  I was \emph{relieved}, disoriented, but those were more states of being than actual \emph{feelings}.



I was muddled.



One task at a time.



Stopping Dragon.



I watched as the suits she'd settled on the ground kicked back into action.



We'd fought Endbringers together.  For a time, the Guild had been one of our biggest assets.  I'd seen what happened when Dragon was taken out of action.  A.I.?  Nothing substantial.  But when her \emph{main} suit was taken out of action\ldots



I saw the way she deployed the suits.  Which was she keeping safest?



One was in the thick of things, creating different types of forcefield to try to mitigate the damage Scion was doing to our side.  Capes had baited Scion out over the water, but the fact that there were less targets in range was counterbalanced by the fact that Scion was more focused on those who were there, and he was hitting harder.  When he hit the water, waves crashed against the shore, doing nearly as much damage as any of his attacks might.  A Leviathan with one arm, one leg, and most of its head missing was perched on the shoreline, apparently mitigating the damage.



There were two more suits on the fray, offering long-range fire.



And one more above the clouds, periodically firing exceedingly long ranged laser beams at Scion.



The drones were making headway.  These capes weren't completely under my control and they weren't the most stable, either.  They were liable to crumble where other capes might stand firm.



Doormaker was recovering his power.  He could make portals, but it was slow.



My first instinct was to regain control.  I reconsidered.



I didn't have time to feel guilty.  I didn't have time to \emph{think}.  There was only a moment where I felt the weight of what I was doing, the knowledge that if this didn't work, I'd set everyone back for nothing.



I opened portals behind Dragon's longest-range ship, the entrance portals above my army's heads.  I began firing through the doors with every individual I could control, creating more portals to seize control of others with every passing second.



More ranged attacks joined the barrage.  Dragon flew out of the way, her ship badly damaged, and I moved the portal, maintaining the assault.



The wreck of the ship plummeted from the sky, and the behavior of the other Dragon-craft changed, as though they'd switched gears.  The drones dropped from the sky once again.



Something told me this \emph{wasn't} a feint.



I opened portals into the Birdcage, and Dragon didn't stop me.  No containment foam came down from the ceiling.



Maybe fifty or sixty members of my swarm had been disabled by the nonlethal measures.  With the Birdcage, I added seven hundred and forty-three individuals to my army.



The nonlethal measures would wear off.  It was a step forward.



I turned to my passenger to sort them out, and I sent a share of them into the fight to reinforce the others.



One obstacle, removed.  Dragon would take time to reboot.  I could disable her in a similar manner next time.



Defeating Dragon this way hadn't been ideal, not completely freeing myself of the distraction and threat she posed, but it beat murdering her.



I turned my attention to the world as a whole, with the idea of recruiting other capes.  I hit a dead end.  The worlds were bleeding together, and it had gotten worse while my attention was elsewhere.  I had to force myself to clarify what I was looking at, to tell myself that the areas didn't make sense.



It took excruciating minutes to get my head out of that sludge, and to make sense of what I was looking at.  \emph{Minutes}, as Scion tore into Alexandria, to convince myself that it \emph{was} all in my head, and that Scion wasn't actively tearing apart reality.



I exhaled slowly, and the exhalation was a shudder.  My throat hurt from the screaming.



The going was slow at first, but it picked up as I let my passenger handle more of the load.  Capes in hiding.  Rogues.  Deserters who had fled for safety in our hour of need.  A surprising number of capes who had no costume, and who had barely used their powers at all, judging by the way it felt when I reached for their abilities.  They were rogues who'd been subtle at best, or rogues who'd gone without powers altogether.



There were the retirees, not \emph{old} capes, but capes who'd been wounded, or who'd dropped out of the scene for other reasons.  Their powers were more developed at their core, but rusty at best.



I reached for the insane, along with those disabled by their powers.  A small few, all things considered.  Glory Girl was among them, in a newly built wing of a home for non-cape invalids.  Something her family had set up, no doubt.



I found members of Bonesaw's Slaughterhouse Nine.  Clones who'd fled, or who'd been left behind, lurking in dark corners, or simply hiding.  A Mannequin, two Damsels that were keeping each other company, a Night Hag-Nyx hybrid, and a Crawler-Breed hybrid.



When I had the vast majority of them, I began looking to other universes.



There were capes in Earth Aleph, barely C-list by our standards.  Sundancer, Genesis, and Ballistic were there as well, the former two in civilian clothes, retired, the latter in a lavish penthouse, fully done up in costume.  My portals opened, and I had control of them.  I left Oliver behind.



Other earths only had a small handful.  No doubt there had been contamination at some point where doorways had been opened.  Whole worlds with only ten capes at most, half of which were case fifty-threes.



\emph{Monster}.



I shook my head a little, blinking.



I found another Earth with a mixture of capes, all incredibly beautiful people, all in what was obviously a global position of power.  Every flag that flew in their world was the same flag, and the gauntlet emblem on that flag matched the icon on a particular woman's costume.  A blue costume, with white fur at the collar, and a heavy cape that would have done Alexandria proud.



I attempted to seize control of them as well, and the woman in blue resisted me.  She spoke, and I lost my hold on everyone in her range.



It was only twenty capes.  Negligible.  But I wasn't going to settle.  If I was going to compromise on any level, it was going to take more than this.



I created a portal, and I ensnared Canary, who was busy rescuing the wounded, flying here and there with her Dragonslayer suit, her arms full.



She set down the wounded, and then she passed through the portal.



She began to sing.



I was controlling her, and it was my song in a way, syllables rattled off at a fast tempo and severe clip, followed by long high notes.  Not English, but not my own muddled speech either.  I could feel her expressing her power through the song, through each intonation and sound.



I brought her close enough to give her the benefit of the Y\`{a}ngb\v{a}n's power enhancer.  I had enough awareness of her power to know how to keep myself safe from it.



I tried again with these foreign capes, in this world where this blue-costumed woman ruled the world, portals feeding Canary's song into their council chambers.



Those same portals let me attempt to reassert control.



An attack from two directions.  She wasn't \emph{immune}, only resistant.  I felt myself assert control.  I understood her power, even if I didn't understand a thing about \emph{her}.  A personal, point-blank trump power, allowing her to tune abilities and defenses much like Scion did.  A powerful long-ranged telekinesis, a compulsion power like Canary's, presence-based rather than voice based, and a personal power battery that let her be \emph{stronger}, for limited times.



Where the hell had \emph{she} come from?



No powers that really made her \emph{amazing} against Scion, but it was an asset.



The others\ldots they weren't weak.  Nothing gamebreaking, at a glance, but they weren't weak.



\emph{Sleeper. } I could see him, sitting on a lawn chair on a balcony, reading a book out loud to himself.



More trouble than he was worth.  I let him be.



One by one, I brought the ones I'd collected to the battlefield.  The prisoners, the brainwashed, the lunatics, the cowards, the monsters and the broken.  They assembled in groups, in the spaces between the other major groups.  In front, behind, above, and below.



Canary's song wove its way out of the portals.  Slower than before, working with the wind and the waves rather than fighting against them.



More doors opened, and more of the ones I'd collected continued to appear.



Teacher was making his way into Cauldron's base, walking past the heroes at the doorway like he belonged there.  He was talking into his phone, mocked up to be like a PRT-issue phone, and the communication was going to every major member of the Protectorate and Guild.



Contessa, for her part, was waking up.



I was shaking, and it wasn't just the tension.  I wanted to sit down, but I knew that if I did, I probably wouldn't stand again.



\emph{My anchors\ldots  The mantle of portals, Tattletale, Rachel, Imp, Grue.}



My old house continued to elude me.  That detail gave me a sinking feeling in my gut.  I reached out for a replacement.  Not my home, then.  My dad's workplace?  No.  Something else, something \emph{family}.



\emph{A quaint old house on a hill, surrounded by rose bushes, a grandmother\ldots  }Not \emph{my} grandmother.  I barely knew my Gram.  I shook my head.  The house on a hill had been a memory of something I'd \emph{read}, once.



It was unsettling, the seeming reality of it, the nostalgia.  If I was a little further gone, could I have clung to it, used something \emph{wrong} to keep my identity intact?



I was still lost in thought when I became aware that I'd stepped onto the battlefield.  I hadn't plotted it.  Had even felt like it would be a bad idea.  Now Miss Militia was turning my way.  Exalt was standing beside her.



Teacher was talking, and they were responding.



He was warning them about the \emph{threat}.



I could see people throughout the crowd.  Protectorate members, team leaders of the Wards.  They were tense.



A voice carried over the wind.  I recognized the \emph{quality} of it, even if I didn't recognize the words.  Glaistig Uaine, welcoming me back.



Crooning.  She was pleased, on a level.  I found her sitting on a mountaintop, surrounded by three of her ghost-capes.



My small army had grown to be a formidable \emph{force}.  Three thousand strong in all.  I had \emph{thirty} layers of portals around me.



Teacher said something, and it was Tattletale who replied.  I could see her, and she didn't look happy.



So many voices, so many things to focus on.



I felt momentarily lost in the midst of it.  I had a large army, by parahuman standards, I was probably strong enough to kill everyone here-



I stopped myself.



Why had I thought that?  I didn't want to kill \emph{anyone}.



Glaistig Uaine continued to croon in my ear.  Was it her?



No.  I was almost positive it wasn't, and I had any number of thinkers at my disposal who could have warned me.



I shook my head a little.



I had a large army.  I was powerful.  I could move on to the next big step, but I wasn't sure \emph{how}.  It was like playing chess, the moves I could make had enough gravity and nuance that I could only make one move at a time.  What to do first?  What wouldn't open me up for retaliation?



It was better if I wasn't here.  I turned to leave, backing through a portal.



Tattletale, in that same moment, stepped outside.  She gazed over at my army, then turned and looked straight at me.



Her eyes were wide.  She looked just a \emph{little} freaked out.



\emph{I don't-  I can't\ldots}



My thoughts stuttered.



\emph{Tat-}



I clutched to every image and object I'd set in my mind's eye, to the tethers that were supposed to keep me tied down.



\emph{I}\emph{t's too soo-}



\emph{Too soon.}



I was running out of time.



Had to \emph{move}.  Had to act.  It was easier, so long as I was in the thick of it.



Glaistig Uaine was the real threat.  She would be first.



Thing was, I didn't like the look of those ghosts of hers.  A woman, one of the \emph{really} crazy looking ones who had a costume that was more for revealing than it was for covering up.  She was warped, twisted by Glaistig Uaine's power until the costume and the body were one and the same, which only made her look more vulgar.



I didn't recognize her, but she looked like one of the crazy ones.



There was a guy, built like a football player in full padding, only it was all muscle.  That muscle, in turn, was covered in armor that had spikes studding it at regular intervals.  The helmet covered his eyes.  He sat at Glaistig Uaine's feet, and he was tall enough that her eyes barely looked over the top of his head.



And there was a woman, so thin she was barely there, a look no doubt exaggerated by Glaistig Uaine's powers.  When Glaistig Uaine spoke to me, it was the thin woman who passed on the message, her lips moving.  Like Screamer, then.



I prepared to make a move, and I felt the danger sense of no less than twelve different capes in my army go off.



Yet I still alerted the ghost in armor.  He moved, lurching to his feet, and he spoke.



Glaistig Uaine said something, and it was a single word, a \emph{hard }word.



He was a precog, and to look at him, he was a defensive cape.



She'd been anticipating an attack.



The thin woman moved, and a current of wind ripped through the air, two feet wide and ten feet tall, less a tornado and more a battering ram.  It flew through the sky, homing in on me.



I moved through a portal, and the column followed.  It hit me like a truck, and I nearly lost my grip on the clairvoyant's hand.



I tumbled.  In a sense, my lack of control over my own body helped more than anything.  I was left panting, but I hadn't tensed up because the reflex simply hadn't been there.  Being limp when I took the hit was better than going tense and tearing something.



The Faerie Queen had anticipated an attack.  She had to know what I'd been doing, how I was operating.  If I used my power\ldots



What did the vulgar woman with the lipstick smirk and creepy white teeth do?



Another column of wind homed in on me.



My army threw barriers in the way.  Force fields, walls of crystal and walls of fire.



The column passed between them like it wasn't even a consideration.  I closed the portal in front of me before the column could zip through.



I watched as it changed course, heading for the nearest member of my army.  I might have been able to do something about it, but I suspected it would have found a way to me anyways.  Instead, I shifted my grip, gripping the young man's wrist, and making him grab mine.  A surer grip than hand-on-hand.



The wind-attack compressed, passing through the foot-wide portal behind them, and it hit me.  Not as hard as the first, because it wasn't as\emph{ large, }but it still hurt.



The Faerie Queen spoke, her voice imperious, echoing in that curious way of hers.  Indignant more than furious, but still with that bite of anger behind it.



The others on the battlefield reacted, and it wasn't to rally against \emph{Glaistig Uaine}.



Tattletale was murmuring under her breath.  Was that-  Was it my name?



The faerie queen banished her wind-witch and brought out another spirit.  I tried to capitalize on the distraction, getting one cape with one of the stronger ranged powers to attack her.  A gravity pulse, a bullet that imploded things at the impact site.



The man in armor moved, and the vulgar woman reacted, creating a circle of rippling air.  The bullet struck the barrier, and the man who'd sent out the pulse promptly imploded, blood showering everyone nearby.



Something indirect, then.  I opened a portal a distance away, and I used Canary's song.



She kept the field up.  I could feel the pain wrack Canary, hear her choke on her words.  She doubled over and coughed up blood.



\emph{A power counterer, a precog\ldots  }and Eidolon, now.



If I'd used a portal, what would have happened to me?  Would it have affected Doormaker or me?  Or both of us?



I didn't feel very stable on my own two feet as I climbed to a standing position.  I had a whole army, and I could lose them in an instant if I simply unloaded on her.



I needed to hit her with something that broke the rules.  Not Foil.  I wasn't willing to risk Foil.  But \emph{something}\ldots



I took control of Alexandria, instead, Pretender.  \emph{Controlling the person who was controlling the manipulative bitch Alexandria.}  I took Legend, who was part of that fight, two foreign capes and Moord Nag.



They were the ones running interference, buying us time to breathe.



Now I positioned them.  As I'd done with my bugs, I lined up the shot.



He took the bait, shooting.  I moved everyone out of the way.



Glaistig Uaine's pets informed her of the imminent danger, and the shield was raised in time.



Smoke poured off of Scion, indicating he'd taken the reflective effect full force.



And smoke cleared around the Faerie Queen as well.  She was panting a little, her ghosts tattered but intact.  I made her stand straighter, and then banished her ghosts, replacing them.  I'd used the distraction to plant a portal behind her.



I opened a portal, passing through, re-entering Earth Gimel.



Miss Militia turned a sniper rifle on me.  I caught her before she could fire.



Then, group by group, I captured the rest of the defending force.  Some resisted, some predicted the attack, but it was a foregone conclusion.  I had enough soldiers, enough tools at my disposal, that nothing here really stood in my way.



I created more portals, until I didn't have space for all of them.  I shrunk them, reorganized.  Where I could find the open space, I tapped other worlds, reaching for bugs.



Those bugs then swirled around my captives, flowing around their feet or behind them, where they wouldn't obscure the view.



I saw with compound vision.  Five thousand pairs of eyes, collecting more with every second that passed.



I breathed with five thousand mouths.



I was adrift in a sea.



My eyes fell on Tattletale.  Panacea was behind her.



She shook her head, putting herself between me and Panacea.



I reached out, my hand trembling.



It flopped down at my side.



\emph{I need her as an anchor more than I need her power}.



Anchors\ldots



My mom's grave\ldots it was in Brockton Bay, right?



Brockton Bay.  It took me a minute to find, more time because I was busy keeping capes out of Scion's way.  Putting them through doorways, bringing them back.  Always being careful to keep the doorways from being touched by his power.



I couldn't find the grave.  No time.



What else?  The mantle of power, of course.



Yes.



\emph{Tattletale.}



And\ldots



I reached out, tried to find others, and I failed.



It would- would have to do.



This was it.  Finally, everyone was working together.



I turned my attention to Scion.





