





\emph{Now for the clin- the clincher.  The ultimate strategy}.



We ran.



My number one priority was to keep moving, keep active.  Things were easier so long as I was moving towards a goal.



I had to get myself sorted.  Wrap my head around the tools at my disposal.  For that, I needed time.  I needed to put distance between us and Scion.



\emph{Stepping up the tempo, have to distract Scion.}



I reached out to Ash Beast, a living force of nature.  It had originally triggered in Matruh, Egypt, and had been roaming since, making its way across Africa.  All of the destructive power of any class S threat, tempered by the fact that it \emph{usually} traveled on foot, and people could see it coming from miles away.  When it reached a settlement, that settlement was usually evacuated.



An unending explosion, a rolling mass of fire and smoke with a person at the center.  Here and there, it took physical form.  Whether it was the fire or a massive leonine claw that tore into the ground, it produced the debris, dust and ash that was its namesake, driven along the ground by the perpetual storm of fire.



Creating a portal to give me access to it was troublesome.  Others had tried to control it before, to steer it in the general direction of their enemies.  Warlords, villains, masterminds.  It rarely worked for long.  When working with power on this scale, chaos had a way of trumping order.  Too much energy disrupted the portals.



I moved a forcefield cape to the Ash Beast's location, and then created a bubble, putting it in range of the being.  I made a portal within the bubble.  More forcefields encased the bubble on my side for safety's sake.  My power operated through the forcefield, and the connection formed.



I identified a young man, at the center of it all, and I could now think of the Ash Beast as a `he' instead of an `it'.  He was surprisingly healthy, but he had a power that kept him in good physical condition, a natural breaker-class adaptation that came with his power.  Energy to matter and matter to energy.



I'd use him first.  If he died, the world wasn't worse off for it.  If he lived, well, I could discard him, leaving him in a foreign earth.



Bringing him through a doorway was hard.  He generated so much heat, and while his shape and form were malleable, they weren't wholly under his control.



In the end, I made a portal, and I used Trickster to bring the Ash Beast through, replacing a chunk of ruined earth.



\emph{Shaping the fire, driving it out to the sides.}



\emph{Shaping the flesh.  From energy to physical form.  Wings.   Catlike legs to spring into the air.}



The Ash Beast lunged into the air, above the water, and he streaked towards Scion like a comet.  The forcefield cape followed, to maintain the connection.



I moved Alexandria, Legend, Moord Nag and the others on the frontline through doorways as the Ash Beast struck the golden man.  Golden light tore into flesh that had been forged of fire, and more flesh was created to replace it.  The Ash Beast tore into Scion, and the flesh was replaced just as quickly.



I created more doorways, moving people out of Gimel in an orderly fashion.  Here and there, I changed the portals around, dictating different exit points to break up groups.



Ranged attackers in one group.  Brutes broken up into several sub-groups.  Thinkers, tinkers, defensive capes\ldots there were a lot to sort, a great many who had powers that needed a half-second to a few seconds to figure out, in terms of classification and application.  With \emph{scores} of these capes, it added up.



Every cape had a place to be.  There were capes who needed something to harvest, who needed materials, and I gave them access to their materials.  There were capes who needed others nearby, and capes who were better if set apart.



I assigned precogs, thinkers and danger senses to the various groups.



\emph{Decentralize, }I thought.\emph{  }If Scion was the established force with superior weapons then I had to be the guerrilla army.  Different groups moved to remote locations, different worlds.  I couldn't let him destroy too many of us in one good hit.



Take stock.  Who \emph{didn't} I have?  I didn't have Contessa, who I couldn't see.  I didn't have the Blasphemies, who hadn't even registered to me because they weren't human, even if they had powers, I didn't have Sleeper and\ldots



Why was it so hard to reach for certain names?



The ones in the cabin\ldots  I'd decided to leave them be.  I was having trouble remembering \emph{why}, but I'd trust my older self on that score.



They were dangerously close to Scion.  If I moved them, maybe-



No.  I had to leave them alone.  Rules, regulations.  I'd set boundaries for myself once, I'd followed them, because I knew how easily I could \emph{slip}.  Those boundaries had been to protect \emph{myself}, as selfless as they might have seemed.  This was to protect \emph{others.}



This was good, better.



Capes who could grant flight\ldots Glaistig Uaine had some.  There was a girl in a red, black and white costume who could grant powers.



\emph{Othala}.



Right.  Othala.  She could give someone else flight.  Send the right people to Scion's vicinity.  Trickster, some defensive capes.  One of the capes who had served under the Blue Woman in that cape-ruled alternate Earth.  He had a power not unlike Gavel's.  Glaistig Uaine offered some offensive power as well, but it was tricky and time consuming to dig for the capes I could use.  She knew them \emph{personally}, I had to find them.



They appeared behind Scion.  Glaistig Uaine distracted, with one ranged cape hitting Scion full-on in the face, another feeding fire into Ash Beast's body.



The Gavel-alike dropped out of a portal directly above the golden man, driving a narrow pole into Scion's neck.  Scion was slammed into the water, quite possibly to the bottom of the bay.



The forcefield cape caught the boy out of the air before he could follow Scion beneath the water.



I opened a portal, then moved the others aside.  Reorganizing, positioning.



Others\ldots who was I leaving behind?



There was a group still in the settlement.  They hadn't all moved through the portal.  I reached for their names.  Right.  Tattletale.  Rachel.  Imp.  Panacea.  I'd taken the others, collected the wounded.  The door was open, but they'd stayed behind, watching the horizon, exchanging words I didn't understand.



Who else?  I'd left the civilians be. I \emph{could }arm them, but I wasn't sure it would be worth the effort.  Bullets could only do so much, and the bigger weapons\ldots



Scion emerged from the water.  I didn't give him a chance to retaliate.  Retaliation could mean putting the cabin in danger.  I hit him, then backed the capes through the portal.



He didn't follow them through the portal, but he did sidestep through dimensions to reach them.  I started to mount a defense, and he lashed out.  I didn't have time to react or give a command; I slammed the portals around the capes shut, and I opened another, larger portal, to take in the beam.



The beam hit the surface of the portal, and only a fraction passed through to strike Scion from behind.  Enough to kill someone, enough to kill \emph{me}, if the beam had happened to touch any of my control portals, but even so, the portal itself took the brunt of the impact.



Doormaker staggered beside me.



The portal was wiped out.  Without any barrier in the way, the beam radiated forward to wipe Ash Beast, the cape with the pole, Trickster, and Othala from existence.



I was left with a decision to make, no time to make it.



Was I going to be moral, or efficient?



Two capes fell in my awareness.  Acidbath was one.  Another was a talented shapeshifter who was in bad shape beneath their moldable skin.



\emph{Shapeshifter}, I made the call.



One expendable asset.  At my bidding, he strode forward through the portal.  The clairvoyant retrieved a tinker device and dropped it through a portal.  The shapeshifter caught it.



Scion pressed the attack, while Glaistig Uaine and her assigned bodyguard managed a fighting retreat to a portal I'd raised behind them.  Had to keep Scion in place, buy time.



I had only a seconds to act, or I'd lose the Faerie Queen.  I'd lost good capes already, so very easily.  Now I stood to lose more.



\emph{Have to-  have to make it worth it.}



Thinking in \emph{words} was getting harder.  Easier to default to thinking in terms of \emph{ideas}.  I wasn't going to throw away lives for \emph{nothing}.  I wouldn't ask others to make sacrifices I wouldn't make, if the roles were reversed.



Maybe they'd disagree.  Maybe they'd tell me they didn't want to make that choice.  But that was our instinctual \emph{self-preservation} at work.  With things at this scale, that kind of thinking was counterintuitive.



Maybe they'd \emph{agree}, if I had the time to explain.  To sit down with them in their living rooms and discuss the ins and outs of things over tea.



But I didn't have the time to ask politely, and too many had already died.  Capes and civilians both.



I'd leave the civilians alone, but it was fitting if I drew on \emph{their} strength as well.



Doormaker was capable of opening the doorways at the speed of thought.  I had multitasking abilities.  I could open them faster.  Not one after the other, a thirtieth of a second passing between each, but \emph{simultaneous}.



I didn't target people this time.  Portals opened across the sky in that foreign Earth that Scion and the Faerie Queen fought in.  As many portals as I could fit in that Earth's sky.



Glaistig Uaine ducked back into the portal, and the shapeshifter I'd left on the ground hit the button.



The portals around Scion slammed shut, and he disappeared from my mind's eye.



It left the shapeshifter locked in the same world as Scion.



An obstacle, a speed bump at best.  I was sacrificing lives for that purpose, putting capes in harms way, and leaving that one cape in an isolated world with Scion nearby.  I'd decided to spend a life that lacked \emph{strength} over the life of a monster.



But that last gesture had bought me time to move the Faerie Queen of the Birdcage to safety.



It had also stopped Scion in his tracks for a few seconds.  If he was focusing on getting out of that universe, on altering his power to decrypt the portals and free himself to move, then he wouldn't be paying too much attention to the portals I'd opened above him.



There were perhaps two hundred Earths in easy reach that had military technology worth talking about.



Two hundred earths with \emph{bombs}.  Every bomb that hadn't been in some secure housing, every bomb that was small enough to drop through the doorway, to plummet to the ground below Scion.



Some would be duds, no doubt, missing an integral component that would be put in place before a bombing run.  But a handful, I suspected, were bound to be nuclear bombs.



He hadn't stepped through into any world I could see.  The bombs had struck home.



My body was shaking.  I wanted to sit down, but I couldn't afford to.



I was hungry, I realized.  Worn out.



But I had to capitalize on our advantage here.  Had to focus on sorting out my army, so this wasn't for nothing.



I broke up the Y\`{a}ngb\v{a}n.  Null/Zero could share powers and he could take them away.  But managing multiple groups was cutting into every group's effectiveness.  Against Scion, I needed more effective powers than a blending of less effective ones.  I set Zero aside, assigning him a group.  Autopilot for now, for a later eventuality.



The tougher capes I had fell into two categories.  There were ones who could take the fight to Scion, like Alexandria or the late Ash Beast, and there were ones who couldn't, like Lung, Menja and Chevalier.



There was a Vietnamese cape with a tinker ability who I hadn't assigned to the tinker group.  He was like Lab Rat, but simpler in application.  Formulas to boost strength and size, turning regular people into hulking monsters.



I put him to work, dosing capes who weren't reliant on armor or anything of the sort.  I left Chevalier alone, and left the Crawler-Breed hybrid be, but I dosed Lung and Menja.



I put Legend and the Number Man with the ranged capes.



Scion emerged, but he didn't emerge into a world any of my forces occupied.



\emph{He- he lost the scent trail}, I thought.



It didn't take him long to find it again.  He went straight through into the world where I'd stationed Glaistig Uaine.



I opened portals.  Every single ranged cape and every single cape with a gun that was at my disposal opened fire into the portals.  The Number Man's power coordinated their fire.



I sensed danger from my precogs.  I parted the group.



Scion moved, and he fired a beam, striking down the center of the part.



Not one of the attacks had hit him.  Though I'd been moving them to safety, the beam had taken out nearly thirty capes.



I counted Lady Photon among the dead, along with Revel.



As if Taylor Hebert were one of my puppets, distant, fractured and broken, I could sense the sick feeling in her gut.  Revel had been someone she'd- someone \emph{I }cared about\emph{.  }Lady Photon had been a familiar face.



\emph{Let's go get that-  Let's go get him}.



My voice, but not my own \emph{thoughts}.



The Number Man had told me the attacks would hit.  That they hadn't meant it was Scion's precognitive ability at work.  The ability to win, to take the upper hand.



But there was a reason he couldn't use it constantly.  It cost him something, drained his reserves.



By all appearances, he'd parried my thrust and struck home\ldots but I'd taken a piece out of him.



The rationalizing felt thin at best.



\emph{Have to do bett-er.}



Scion was screaming, still.  A roar, a kind of fury.



Tattletale had described him as human.  That meant human weaknesses.  Weaknesses he hadn't learned to adapt to.  When he got angry, it was the fury of someone who'd never learned to hold back.



I put targets in front of him, and he took the bait.



A front line of the hardiest capes, decoys and projections to draw him in.  Then, while he was closer, I was free to move in the heavy hitters who \emph{weren't} upwardly mobile.



Lung, hulking out even before his power kicked in.  Menja, Chevalier.  A dozen capes I didn't know.



Had to mix it up.  Raw physical strength, then a cape who was strong because of a telekinetic bubble that surrounded them.  More raw strength, then explosive power like Hoyden's.



Move them in, then move them away.  Use their powers and other powers to give them the mobility.  I had two capes that could \emph{assign} danger sense to protect things, alerting them when the subject was in danger, though the two powers were rather different in practice.  It was a way around the fact that I couldn't predict Scion himself, and I made the most of it, switching their targets of choice second by second.



I could feel the fear of the people I was sending into the fray.  Hoyden's fear was like the scared-little-girl fear I'd experienced while concussed, wracked with pain and helpless at Bakuda's feet.



But she could hit Scion, and I needed people who could hit him.  I needed every iota of strength I could squeeze out of these capes.



I watched the world through Defiant's eyes, and I saw the combat analysis program drawing wireframe models over the battlefield, trying to take in all of the details of the capes I was sending into the fight, predicting Scion's most likely actions.



I watched with the Number Man.



I watched with precogs.



Scion wasn't inherently predictable, he wasn't capable of being read, but I needed \emph{some} cue that would let me guess what he'd do next.



Telekinetics stood by portals.  The Blue Woman and Parian were among them.  When I saw opportunities, I used them to move capes further, faster, to get them out of the way.



Scion's rage was reaching a crescendo.  The screaming was increasing in volume and intensity, the movements more aggressive, the attacks broader, less focused.  A fist flew past Chevalier, followed by a blast that might have wiped out a neighborhood, if the capes had been in a city.  He was grazing capes, failing to land a single heavy blow, and it was pissing him off.



It didn't help that we were \emph{hurting} him.  He could adapt, but he couldn't adapt when the same attack wasn't used twice in a row.  It put him on the defensive, keeping him on his toes, and every attempt he made to strike back failed to do more than clip people, injure and wound.



I knew it was coming.  Retaliation.  Even before the precogs gave me any forewarning, I was moving to react.  Portals opened wider, telekinesis pulling the attacking capes through if they couldn't move fast enough.  Forcefields and other measures flew up to surround Scion, mitigating the damage.



He radiated light, and the light that escaped the barriers seared and melted the flesh of the offensive capes, as well as the telekinetics and defensive capes who happened to be standing in the wrong place.  Translucent and transparent forcefields didn't even slow the light down.



I began shutting the doors.  Alexandria and various projections flew in to take Scion on.  Ursa Aurora, expendable duplicates\ldots just needed a second.



So much \emph{pain}.  I could tell how much damage that had been done even before I did any headcounts.  People were suffering, and so long as they were under my control, they were helpless to express the fear and agony they felt.



Instead, they were quietly stoic as their wounds wept fluids and burned with traces of the golden light.  I put the few healers I had to work.



They hadn't even started when Scion used the \emph{real} attack.  I could see him move through Alexandria's eyes.  Through \emph{Pretender's }eyes, rather.  Arms flew out to the sides, and then he \emph{clapped}.



I only managed to shut Alexandria's portal a fraction of a second before his hands made contact.



One strike of palm against palm, and the shockwave swept past us as if in slow motion, moving past every portal in the area that was still open.  It passed through flesh, and it \emph{stilled}.



It was the same effect he'd used to quiet Leviathan's waves, the same effect that had frozen floodwaters in their tracks and the same ability that had given him so much presence.



Objects in motion \emph{stopped}.  Portals winked out, warm things plummeted in temperature, cell and neural activity was interrupted.  Blood stopped in people's veins.



Every cape that had been touched by this \emph{stillness} dropped to the ground, lifeless.



I could feel the horror that was experienced by the bystanders.  I knew that, given the choice, most would be running.



But there was no reaction.  Each and every one of them was grim, resolute, taking care of their injuries, getting to people who could tend to them or helping others.



Rank and file, a dozen capes with electricity powers entered the area with the capes who'd succumbed to the stillness.



They'd stopped, and an object at rest remained at rest.  I just- I needed to get them moving again.



A jolt, the electricity controlled by the capes in question.



Nothing.



I pulled Bonesaw away from the tinker group.  I couldn't devote the focus necessary to use her power in any detail.  I \emph{could} have left her on autopilot, but I wasn't sure that was much better.



I revoked my control over her, leaving in in the middle of the room with the capes Scion had \emph{stopped}.



Then I turned my attention back to Scion.



I couldn't \emph{dwell}.  Couldn't let him turn the tables and put me on the defensive.



He was tearing into Alexandria.  Literally.  But she doggedly held on, delivering one crushing blow for every pound of flesh Scion ripped from her midsection.  He was roaring as he did it, teeth bared, face contorted.



The nature of his attack, the stilling, it didn't fit.  Not in tune with the anger.



It had been another use of his `automatic victory' power.  Looking to the future, seeing how he could do the most damage, then following through.  A feint, followed by the critical blow.



The good news was that it meant I was getting the upper hand, forcing him to take a shortcut to get out of it.



The \emph{bad} news was that I was almost positive I couldn't win if things continued in this vein.  My precogs weren't countering his precognition, and he was blocking all direct views of him, forcing me to emphasize \emph{indirect} predictions where I focused on the damage he was doing and the people he was threatening to kill.



With each exchange, he was doing too much damage to our side.  If I had five times the capes, if we'd been working together like this from the beginning, then \emph{maybe}.  But not like this.



\emph{Same strat- strat- same tactic as before, just to buy myself a little time to think.}



My telekinetics, injured or otherwise, worked their magic through the portals I opened, this time focusing on the munitions that \emph{weren't }easily accessible.  I moved ICBMs through a spatial-warping `lens' that let it fit through a doorway, unloaded crates of grenades and TNT with telekinesis, and I watched it \emph{rain}.



The explosives were halfway to ground when I had Alexandria use another dimension switch to force the portals closed.



I needed to consolidate my strength.  I had capes gathering materials.  Moord Nag was among them, one of the scariest warlords of Africa, now traveling between dimensions to scavenge from the dead, her pet shadow devouring mountains of flesh from mass graves and battlefields, swelling in size.



Lung was shrinking, keying down after I'd pulled him away from Scion, but he still had the raw strength from the dose of distilled brawn I'd given him.



\emph{Coordinate}, I thought.



I couldn't be moving capes with telekinesis.  There had to be other assets.



\emph{Sifara.  }A chief\emph{ }member of the \emph{Thanda}.  I'd taken to thinking of him as `Orbit'.



But Orbit wasn't quite it.



His power required him to have a strong reference for those he worked it on.  Eyesight alone didn't work so well, because eyesight was faulty.  His \emph{preference}, for a strong connection, was to touch individuals.  Failing that, he worked by eyesight alone.



I didn't need to go that far.  I could see through a hundred pairs of eyes at this location alone.



A cape formed a ball out of stone.  Roughly the size of a tennis ball.



One by one, \emph{Sifara }connected the capes around us to the ball.



Sifara's power maintained spatial relationships.  He moved the ball, and every cape he'd connected to the ball moved a corresponding amount.  When he turned the ball, the connected capes rotated around the ball by equal degree.



We'd used it against Khonsu in our first fight, anchoring ourselves to him so he couldn't teleport away without bringing us with him.



Now we were going to use it for the opposite intent.



Labyrinth and Scrub, the same pair that had made the portal in Earth Gimel, made more portals.  The dimension switches wouldn't work forever, and I'd pretty much but there were options for future attacks.  There were more explosives, but nothing \emph{big}.



I needed a focus, a weak point I could capitalize on.  To those ends, I needed to buy time to work and I needed to bait him into getting angry.



Between them, Labyrinth and Scrub began making paths to other worlds.  I watched as they paged through the available options.



Scion emerged from the other world, having broken down the barrier we'd set.  Fragments of Alexandria's body tumbled to the ground, more like a statue than flesh.  He had to flex his hand and use his power to free it of the left side of her skull.



He'd suffered for a few of the big hits we'd delivered.  His flesh remained pristine, golden, but there were folds and scraps here and there where his damaged flesh had been stripped away and remained in place around the creases of his body after the replacement flesh had come in.



He came out swinging, obliterating two continents on two different worlds before he found \emph{us}.



One rotation of \emph{Sifara's} ball, a row of doorways, and the capes were pulled backwards through the portals, which closed promptly after them.



The debris hadn't even settled when I had \emph{Sifara} move the ball again, erecting more portals to send my capes into the battlefield.  Brute force, capes who could tie him down, capes who could take a hit or two.  I kept Lung in the fight, holding him back for later, when he'd be exponentially stronger.



As strategies went, it would hold for at least a little while.  Scion's patience seemed to be getting shorter and shorter, and I was on guard for the next retaliatory strike.



My heart was pounding, my mouth dry.  This was looking grim, each exchange hurting my side more than it hurt Scion.  Was there an out?  A chink in the armor?



I'd collected all of the tinkers in one place and I'd put them on autopilot, a vague, nebulous goal in mind.  To get them working together, I'd used Zero of the Y\`{a}ngb\v{a}n to tie them together as a group, splitting their powers.



A few hundred tinkers, each with a mix of tinker powers, all working on a singular project.



I could sense it, using the Clairvoyant and Doormaker both, using Labyrinth and Scrub.  The solid space between worlds.  A space that Scion had altered somehow, blocking off.



Facing off against that, I'd had them build something roughly the size of a house.  There was a gun build into the construction, but it was snub nosed, stocky and unimpressive.



I gave Defiant the honor of pulling the switch.



The machine whirred to life.



Through the Clairvoyant, through Labyrinth and Doormaker, I could sense the machine reaching through every available world.



The energy was focused on a single space, but it filled that same space in each of the worlds.  A pressure of sorts started to form.



It would take a minute.



I sent Moord Nag in with the other heavy hitters, relieving the force that Scion was fighting.



\emph{Sifara} moved the ball, moving Moord Nag a distance forward.  Her pet shadow \emph{Scavenger} loomed, as large as it had ever been.



And Moord Nag promptly had a stroke.  I watched as Scavenger dissipated into smoke.



\emph{Wha- what?  Why?}



I reached out to Moord Nag, and I could feel the damage being done.  I moved her back just as I'd moved her forward, shifting more capes onto the battlefield to deliver some ranged fire.



\emph{Why?}  I was stunned, and putting my thoughts together in regards to \emph{this} was like trying to swim in molasses.



Had to act, instead of thinking.  \emph{Investigate.}



I used my ability to read the physical states of the creatures I controlled, reading my swarm much as I'd check a spider's level of hunger, its health, fertility or the amount of venom available.



Almost across my entire swarm, people were threatening to lose their minds.  Literally.



It was stress, a factor I hadn't taken into account.  I controlled their bodies, but I didn't control their minds.  They were bystanders, watching this all unfold, and even though I regulated their heartbeats, kept their breathing level, the mental stress accumulated.



There were exceptions in every category, but I could assess my gathered army with broad strokes of the brush.  The thinkers were coping best, the tinkers nearly as well.  The masters struggled the most, followed by the shakers and breakers.  The rest fell in some middle ground.  Moord Nag\ldots my control over her had apparently tapped into some kind of trauma or phobia she had, so she'd been the first to reach some kind of fever pitch in terms of the buildup of stress-induced chemicals and reactions.



I was killing my own minions.



I moved quickly, scrambling to get measures in place before I lost any more.



An open portal and a telekinetic let me move Moord Nag to the only available, capable healer I had available.



I sent her to Panacea, still in the company of Tattletale and the Undersiders.  Panacea bent down to help her.



I brought Canary to me, and she began singing, a high, sweet song, almost like a lullaby, her voice carrying through the same portals that connected me to my underlings.



I was halfway to my \emph{next }step, managing the tinkers, when Panacea reacted, backing away from the dying woman, shaking her head.



\emph{You still- you still don't use your p-power on brains?  }I thought.



She'd had a setback, creating \emph{me}.  Now the old fear was back in full, at the most inconvenient time.



Tattletale was speaking.  Her voice was gentle, soft.



It was awfully nice to listen to.  Reassuring, even if I didn't understand the words.



Then, breaking me from the spell, Scion moved his hands, readying for a clap, and I shifted everyone out of the way.



Scion \emph{flew} instead, flying into one world, just as easily as a plane might fly \emph{left}, \emph{forward} or \emph{down}.



I could track his movements with the clairvoyant.  As multidimensional as it was, I could trace a trajectory.



He'd used his `automatic victory' power again, and he'd targeted me.



If he'd used it to \emph{find }me, there was no escape.  If he'd used it to \emph{find and kill me}, it was all over.



Was he that complex?  Did he think forward to that degree?



I ran anyways, turning my attention to the tinker's machine.



The gibberish text on the screen had turned red.  Failure.  The combined strength of all of the tinkers who remained, Bonesaw excepted, and it had failed.  There was no way to get to the space Scion had sealed off, no way to his `well', where he drew all of his resources from.



My heart sank.



\emph{That was my best guess}, I thought.  The mental stutter wasn't there, but the stutter only tended to hit me when I thought about \emph{nice} things, about peace and familiar people and all the rest of that stuff.



The best means of attack was to go for the weak point.  To cut the jugular, to stab the heart, to go for the eyes, damn it.  Scion's well was the closest thing to a weak point that I could imagine, but he'd secured it.



I'd told myself I'd know the strategy when I saw it.  Targeting the well hadn't been that strategy, but it had been a piece of it.



I moved capes away, stepping through the portal Labyrinth had made, then having her change the channel, masking our `scent', so to speak.  I moved Case fifty-threes into the area to mess with Scion's ability to sense things.



He still pursued.  I couldn't move fast enough, even as each limping step moved me to another universe.  Something about the way the portals opened, even if I closed them, it was like I was breaking ground for him to travel.



\emph{This- this is the trouble with being on top.}



\emph{You're all alo- alone when it counts.}



I put capes in his way.  He swatted them aside, flew out of the way, and closed the distance.



I felt sick.  The shaking was as bad as it had ever been, and there was a coldness inside of me that made me wonder if I was in shock.  My thoughts were barely coherent.



I had Glaistig Uaine, I had her Eidolon shadow-puppet.  They worked as a pair to hit Scion with the heaviest attacks I could find at a moment's notice.



For all it mattered, they might as well have been a kids on the schoolyard, sticking their legs out to trip someone.  Scion found his momentum again.



Panacea was healing Moord Nag.



I reached for the warlord, bringing her to me.



Scion struck her aside before Scavenger could swell to his full size.



\emph{Too little, too late.}



If not brawn, then traps and tricks.  If he wanted to charge right at me\ldots I'd do what I did against Echidna.



I stopped and turned around.



\emph{Foil}.



\emph{Cuff}.



They stepped out of portals, one to my left, one to my right.



Cuff to shape a sheet of metal into a giant razor blade, Foil to rig it with her power, setting it in Scion's way.



I gathered every precog I had, putting them within my sixteen foot radius. I \emph{gestalted }them with Zero as they made their way through the doorways, forming a Y\`{a}ngb\v{a}n contingent of future-seers.



I wound up with a young teenager right in front of me.  Brown haired.



\emph{Dinah}.  I turned her head to see her face, and she saw me in turn.  I could see myself in her eyes.



\emph{I'm sorry}.



\emph{You're different.}



I felt a chill.



\emph{No time.  }I opened a portal to send her away.  She wasn't any use, and\ldots and I couldn't even articulate why I couldn't keep her here, when I'd keep the hunchbacked Case fifty-three from Boston and the crazed villain I'd spirited away from Monaco.



I banished Foil as well, sending Cuff and Canary after her.  They'd keep Tattletale and the others company.  I disconnected them from my control network, giving them free will once again.



\emph{S-s-sen- Sentiment}?  I'd told myself I'd be logical.



Was I succumbing to emotion and impulse, letting her go?  Or was I sticking to my rules, my promise that I wouldn't leverage her?  Logical, emotional, something else altogether, it didn't matter.  I wasn't exactly balanced.



I felt very, \emph{very} off balance, as a matter of fact.



It was the same as before.  The precogs weren't strong in this circumstance, but if I could get one \emph{glimmer}, put this thing in the right position, move it, do \emph{something} to get in Scion's way\ldots



He appeared, flying straight for me.  The group would have to do without her song calming their emotions.  Hopefully nobody else would stroke out.



With the precog \emph{gestalt, }I could somehow get a sense of how Scion was going to move.



It didn't matter.  His hand glowed as he struck the flat side of the razor, and it dissolved into a ruin of glowing fragments.



I could see him in person for the first time since this fight had started.  My own vision wasn't as clear as some of the other eyes I'd used to look at him, and I had trouble keeping my eyes fixed on a single spot.



My head turned, and I looked at the others.  Tattletale, Imp, Rachel, Panacea, Foil, Canary, Cuff\ldots



I saw Imp's lips move.  She was saying something.  It was probably very clever.  Something funny and witty and totally out of place.



Or maybe she was saying the same thing I'd said when I'd parted ways with the group as a whole.



Rachel was silent, but she sort of dropped to her knees behind a giant, monsterfied Bastard, who was lying on his side.  Her arms wrapped around his neck.



And Tattletale-



She put her hand to her mouth, then sort of made a sweeping gesture with her arm.



It dawned on me that I had no idea what the gesture meant.



\emph{Be-be-because you can't le- let me have even that}, I thought.



Scion stepped forward, hand still glowing, and he blocked off my view of the group.



The plan had been simple.  Thanks to Teacher's underling, I'd been able to retain my memory of the trigger event.  Scion had censored the most pertinent details, but he'd left one vital weak point in the midst of it.



He'd analyzed us as a species.  He'd seen how we functioned, the strategies we could employ, and he'd set himself on a path.



But that path, I was almost certain, was predicated on the idea that we couldn't work together, that we couldn't bring our full strength to bear.  We were too chaotic a species.



He'd made one mistake I knew of, he had predicted a future where he would meet his partner and then pursued that future, only to meet the brain-dead version that was in Cauldron's base.



I'd tried to help the same happen for the \emph{other} future, running, using the dimension encryption, they were the best thing I could come up with in terms of putting Scion in a world where he saw himself as the only one standing.



He closed the distance, and I couldn't get my thoughts in order to convince myself to leave, to figure out what resources to tap to get myself away.  Teleporters, but which one?



Scion put a regular hand around my throat, and the question became irrelevant.  It was surprising, just how small his hand was.  Larger than average, but\ldots he was still the size of a \emph{person}, for all his presence.



He hadn't killed me outright.



\emph{H-he wan- wants me to show fear}.



His grip tightened, leaving me unable to breathe.  I clutched the clairvoyant's wrist.  When that wasn't enough, I used the meager thread I'd managed to gather together to bind our hands together.



I wasn't in the most lucid state to begin with.  Reality began to dim around the edges as oxygen deprivation got to me..



\emph{Slipping}.



It hadn't been enough, in the end.  It had been a three point plan.  Pushing us towards a point where we were all well and truly united against a cause, doing what I could to trick his future-sight into thinking he'd fulfilled his mission, and finally, targeting his weak point.



The weak point hadn't been available to target.



I might have come up with better, but it had only crystallized after I'd lost the ability to communicate.  I operated best when I could alter my strategy on the fly, but that ship ran aground when I was steadily losing my mind.



Tattletale was saying something, Panacea responding, her hand on Bastard.



Tattletale snapped something in response.



As if in a dream, I could see Foil raise her arbalest.



I moved bugs, forming a barrier between us.



She hesitated, then lowered the arbalest.



I relaxed.  \emph{It woul- wouldn't work a- anyways.  }\emph{N- no use having them die with me.}



But Scion had seen.  I saw his expression change.  Contempt, tight-lipped anger.  It looked \emph{wrong}, his face so unused to showing emotion, his emotion as intense and unfiltered as it was.



He was aware of his surroundings in a way that wasn't entirely human.  Still gripping my throat, he turned, raising his glowing hand in their direction.



\emph{No.}



I still had access to my network.



But I couldn't \emph{think}.



\emph{C-}



\emph{Clo-}



\emph{Close the portal.}



The doorway slammed shut.



Scion took one step, bringing me with him as he advanced between worlds.  The movement made darkness sweep over my consciousness.  I very nearly lost my grip on the clairvoyant's wrist.



He now stood opposite the Undersiders.



Foil started to raise her weapon, slowly.



Scion blasted it to smithereens.  Foil clutched one ruined hand, dropping to her knees.



\emph{I have tools.  I have\ldots what tools?}



Tattletale spoke, her voice low and casual, almost flippant.  She was talking to someone else, I was pretty sure.



Panacea responded, again.  A shake of the head.  She had tears in her eyes.



Moord Nag?  No.  I'd moved her to try and stop Scion.



Dinah?



Dinah watched from a corner, her arms around her knees in a position very similar to one of the first times I'd met her.



He pointed at Rachel.  His first target.



In that instant, it stopped being about stopping him.  I just needed to interrupt, to buy even two seconds.



For the third time, I tapped into every ranged cape I was controlling, and I opened portals around us to give them windows to shoot through.



Number Man to calculate, to aim the shot\ldots  They fired, every cape that could shoot \emph{shot}.



All with the objective of getting Scion to step out of the way, to do another sidestep with that future sight of his.  Even if it was followed by yet another devastating counterattack.  I just wanted him to \emph{miss}.



It didn't work out that way.



It struck home.  Every shot I'd lined up with the Number Man hit Scion.  Multiple directions, even some from above, they hit his flesh with enough force that I was thrown to one side.



Priorities.  Rachel-



Untouched.



The others were fine.



The clairvoyant\ldots our fingers were only barely touching.  The thread I'd wound around our hands had snagged on my armor, caught on the skin of his thumb and nearly tore the skin off.



It hurt like a motherfucker, but he wasn't in a state to complain.  Still in my control, still in contact with me.



For my part, I was coughing violently.  I was maybe at \emph{more} risk of blacking out than I'd been with Scion's hand around my throat.



I fixed my grip on the clairvoyant, then picked us up.  The ground was scarred where shots had grazed Scion and touched earth.  It formed a loose circle, with two spaces where the shots hadn't touched.  One space for me, and another for the Undersiders.



Why had \emph{this} barrage worked when the others didn't?



Had to buy time, make space.  I opened doorways, siccing capes on Scion, driving him out of the building.



What was different?  I hadn't added anything to the group.



I \emph{had} taken something away.



I looked at Foil.



I took control of her, had her bend down to grip a rock.  I channeled it with her power.



A moment later, I brought Ballistic through.



He used his power on the rock.



I was already moving the group to safety when Scion evaded the incoming projectile.



His future sight power wasn't like Contessa's.  Narrower, lacking imagination, but he'd set up \emph{contingencies}.  If X happened, then the power would automatically kick in.



Apparently the cost of being hit by Foil's power was worse than whatever it cost him to use that power.



Not a magic bullet, but it was a good fucking thing to know.  Could I break it?  Abuse it?



We retreated to an empty city in Earth Bet.  The group kept a safe distance from me as we half-ran, half-jogged through.  A bubble of empty space surrounding me.  My portals flickered open and shut around me as I moved, keeping everything essential in my range.



He was beating the capes I was throwing at him, and I wasn't entirely sure what I could do if and when he killed the last of them.  Bonesaw had finished reviving the people who'd been stopped\emph{, }and was working on the wounded, but that wouldn't give me much more in terms of a frontline.



Conversely, if I pulled them back, I was leaving Scion free to do as he wished, and his \emph{previous} patterns suggested he'd revert back to his last priority target.  Me.



\emph{Need- need- need- need-}



The thought stuttered over and over again, a refrain.  It was like trying to move a leg, only to find it cuffed to the other.  Except it was my brain.



\emph{Need- need-}



I shook my head like I was a dog drying itself.  \emph{Think- think straight}.



Tattletale asked Panacea something.  Panacea made a side-to-side movement with her head.



Imp made a wry comment.



The sense of \emph{distance} that I felt was enough to rock me.



As before, it was in the quiet moments that I realized how much I'd lost during the action.  I'd been slipping, my vision getting narrower.  I should have been able to take it \emph{all} in, but the worlds were blending in together.  The clairvoyant was like a drug, and I was building up a tolerance of sorts.  Colors bled together like watercolor, images started to merge, and I wasn't able to focus on more than a handful of things at a time.  The only crutch I had was that I could see what my swarm saw.



But the Clairvoyant was only giving me the ability to \emph{function}, at this rate.  I could turn my attention anywhere, still set down portals in different worlds, but it was getting slower and slower.  Barely a consolation.



I was losing it.  I was almost out of time.



The \emph{certainty} I felt in that was enough to kick me into action.



I didn't even look to my teammates as I stepped away, opening a door to step onto the upper end of the beach.  Water crashed around my feet.



I organized the tinkers.  Changing their job.  A weapon, instead.



I collected some of the capes that were harder to employ, and I began pairing them up.



Halo.  Sundancer.  A handful of masters with projection powers.  A cape with a giant mask.



All powers that \emph{made} stuff.



A ring of razor-sharp gold that produced forcefields and lasers.  A miniature sun.  Soldiers of stone.  A golden mask.  I had each of them make the individual objects as big as they could get.



I retrieved Chevalier, and I did the same with his cannonblade, raising it to its maximum capacity.



Then I accessed Vista.  And I made it all \emph{bigger}.



I pulled the capes out of the way as the various weapons entered the fray.  The sun was as broad across as a skyscraper was tall, the halo was only twice its usual size, firing a substantially sized laser.  Scion avoided both.



Chevalier's weapon should have been too heavy to lift, but he didn't seem to care.



He shot Scion, and Scion was consumed by the sun.



\emph{Everything counts}, I thought.  If we couldn't get to Scion's well, then we had to hurt him on \emph{this} end.



He wasn't content to stay on the defensive.  He turned his attention to the group that was projecting the effects, to Vista, Sundancer, Ballistic, the masters I couldn't name.



Which was the moment the Endbringers made their move.



The Simurgh plunged from the clouds, hitting Scion.



Leviathan, healed a touch, emerged from the water.



Bohu rose from the earth, going from a human sized head and shoulders at eye level to a tower.



Tohu, for her part, had Glaistig Uaine, Eidolon and\emph{ }Myrddin's faces.



The Endbringers, come to the rescue.  I \emph{wished} I could have felt relieved.  It was a reprieve, a chance to get our footing.  But there was an ominousness to it.



Like I'd told Doctor Mother, I'd\ldots



I reached for the memory.



\emph{It- it's humans who win this.  Not something abstract, not- not something we don't understand.}\emph{We win this with our own strength}.



Even if I had to make us.



I gathered my army, bringing them to the battlefield.  I spread them along the length of the beach, keeping them connected to the little round stone that \emph{Sifara} held.



If Scion turned on us, he could pull us away to safety at a moment's notice.



I'd lost people, I had more hanging back.  The tinkers were still finishing the gun.  But I had an army, and I wasn't about to lose any more people if I could help it.



I began to organize another barrage, aiming with the Number Man, using Doormaker's portals-



I didn't fire.



Instead, I watched as Scion's partner came to life.  There was only one growth at first, like a stem, a human-sized body, pure white.



The rest bloomed forth beneath it.  A garden of body parts, hands, stretches of flesh, a maze of parts, all interconnected, all flowing from the piece in the center.  All of it \emph{alive}, this time.  The garden, as Golem had said.



Hands turned to gesture, and flames rose from fingertips.



A moment later, \emph{ice}.  Experimenting, testing powers.



Then it \emph{spoke}.  A soft voice that somehow seemed familiar.



Scion's companion had been gray, this one was white.  This wasn't it.



A \emph{third} entity?



I stared, my blood running cold.



Scion tried to float down to it, fighting almost\emph{ tooth and nail} with the Endbringers to get to his new companion.  Even in the midst of the fighting, the mood was entirely different.  The rage had given way, gone.  I could sense shock, bewilderment\ldots



He reached out, almost as if he were \emph{afraid} to touch it.  To touch \emph{her}.



Where had it come from?  I used the clairvoyant, tracing it back to the origin point-



I realized it at the same moment Scion did.  Our emotions at our simultaneous realizations couldn't have been more different.



I had to wrack my brain, struggling to find the word in the muddle.



\emph{B-bastard}.



Scion howled.  Not a scream of rage this time.  Something else.



It wasn't an epithet.  The third entity was \emph{Bastard, the wolf cub}.  Grown large by the bizarre interaction of Lab Rat's formula and then cosmetically altered by Panacea, given a handful of special effects.  No doubt coordinated by Tattletale.



Scion's mad sorrow was so thick on the air I could almost \emph{taste }it.



I used \emph{Sifara} to pull everyone and everything in the area away before Scion could retaliate.  Scattering them to different worlds with portals.  I used case fifty-threes to break the so-called scent trail to Tattletale and the others.



Scion shattered the shelf of land that New Brockton Bay stood on, and I watched in horror as the cracks moved radiated towards the cabin.



I moved Ziggurat out of a portal, and I used her power.



\emph{Sl- sl-}



I shook my head before I could get caught up in another mental loop of failed, stuttered words.



A fissure opened up.  The cracks stopped twenty feet short of the cabin.



Scion didn't hold back, entering another world, dealing just as much damage, then moving to the next.  It became all I could do to keep my swarm out of his way.  Even with Sifara, even with the doors.



I couldn't think straight, because I couldn't really \emph{think}.  Not coherently.



But I knew, on an instinctual level, that we'd homed in on the weak point.  We just needed to drive it home.  I reached out to seize everyone, opening full-size doorways so I could move them all to one place.



It was when I was opening \emph{my} door that the portals started winking out.



It was like watching a blackout take hold over a city.  Lights going out, sections of apartments at the same time, then buildings.  Not all \emph{even}, not quite logical in flow, but close.



And with every other light that went out, I lost a member of my swarm.



The portals shut en masse, ten by ten, a hundred by a hundred, the furthest one first.  The ones next to me would disappear in seconds.



I looked at Doormaker, who was staring into empty space.



The realization dawned on me.



I'd spent it all.  Too much, pushing it too far.  The well Doormaker drew from in using his power had just run dry.





