





\emph{I had a choice to make.  Into the thick of things, or-r h-hang-hanging b-back?}



What I'd done, taking control, using people like sacrificial pawns, I'd made enemies.  I'd offended the pride of countless villains, of heroes, even.  I was a kill-on-sight target.



I could sense the doorways closing.  Only the ones close to me remained open.  Though `close' was a hard label to apply when talking about dimensions.



I turned to my old standby.  I gathered my bugs, drawing them through the portals that remained, gathering them at my destination.



I stepped through into the cloud.  A rooftop overlooking New York, Earth Bet.  \emph{My} New York.



It hadn't been a conscious choice.  An impulse, really.  Maybe there were cities that were more fitting, but this was a city at the center of modern civilization.  Or it had been.  If this was going to be our final staging ground, then it was as fitting a choice as any.  It was heavy with resources that every parahuman could use, unoccupied.  Intact enough to still look like a \emph{city}, damaged enough to remind us of what was at stake.



With the clairvoyant, I could see the parahumans around us.  They hadn't scattered, and were still holding formation, more or less.



For the time being, we were holding fast.  Scion was still engaged with the Endbringers in Gimel.  We had seconds, a minute or two if we were lucky, to catch our breath, to think, plan and communicate.



If we were \emph{really} unlucky, we'd have even longer.  Long enough for people to talk themselves out of this.  Long enough for trouble to find me, for the Birdcage capes I'd unleashed to cause trouble.  The only reason things down there on the streets were quiet was because people were still reeling, trying to process, because they were in organized groups and breaking from that organization in times of stress was \emph{hard}.



Cults and religions and frat- fratern- \emph{clubs, }they held together because of the power of the \emph{group}.  We were social creatures in the end.  Easier to be one tinker in a small army of tinkers than a tinker all alone.



Heads were turning my way, a few fingers pointing.  Angry mutters.  Clairvoyants, precogs, people with future sight, all of them finding me.  If the lynch mob came for me, there wasn't a lot I could do.  Glaistig U- the Faerie Queen was among them, and she was \emph{mad}.



If she turned her power on me, hit me with anything \emph{close} to what she'd used while I was at the height of my power, I was a goner.



There were a \emph{lot} of capes out there who didn't like being made into puppets.  I suspected that more than a few of them had been victim to it in the past.  Yet others were used to being the ones in control.  Lung, Teacher, the child surgeon.



I counted myself lucky that I'd made it even this far.  That things \emph{hadn't} devolved into chaos the moment the leashes came off.



I'd set myself apart, a little distance away.  The original plan had been to maintain a vantage point where I could watch the battle unfold.  Now it was a refuge, as if capes who could bring cities to their knees hesitated to expend the time and energy to close the distance to me.



I dropped to my knees, still holding on to the clairvoyant, much as I'd hold on to a life preserver while underwater.



Standing was hard.  I needed a chance to rest, to think.



Except \emph{thinking} was harder still.  I was a husk, and things were rotting from the inside out.  I'd hoped I'd recuperate some when I had less people in my control, but it didn't seem like it worked out that way.  Damage done was damage done.  One section of my brain was swelling or creeping out to take over other sections, like it had overwritten dog-girl's social perceptions.



If I could have talked, if I could have communicated, I could have told them.  I could have explained how we could make it all work if we just worked together, if we \emph{coordinated}.  I would have offered myself up for them to do with as they saw fit, if they'd just cooperate \emph{now}.  I'd made the choice for others, sacrificing them rather than letting them choose to sacrifice themselves.  If someone in that crowd was angry enough to give me a fate worse than death, it was probably deserved.



Though probably not equitable.  I moved my hand to my face, the clairvoyant holding my wrist.  I'd taken my mask off at some point.  When had I done that?  My hand ran clumsily down past my eye, my cheekbone, nose, and mouth, every movement trembling.  It didn't feel real.  Like it was a mask I was wearing.



I dug my fingernails in as I caught my lip and chin.  Numb.  I could \emph{feel}, but it was so small a sensation compared to all of the people I'd been controlling.  I saw it from a distance, to the point that I felt like I was barely \emph{there}.  I'd be willing to sacrifice myself if it meant saving \emph{everything}, but that wasn't much of an offer, when my life was already pretty much gone.  I didn't have anything left.



Not that I was free to suggest it, in any event.



I would have explained my strategy.  A way to win, if we could get the pieces in motion.  I would have rallied them, tried to get them on board.  Even told them, knowing I'd be gunned down an instant later.  But I was mute, incomprehensible.



There was only one option left to me.  One I didn't like in the slightest.



I shifted my position, and I sat on the edge of the roof, my bugs thick enough around me that a sniper would have a hard time taking a shot.



I waited.



The assembled capes below were getting more restless.  They spoke different languages, finding others in their number who spoke the same.  Voices were tight with anger and stress.  Some of it would be directed at me.  Others\ldots



There was an advantage here.  Another reason they hadn't scattered.  So much of our dwindling morale was due to the fact that we hadn't been able to \emph{affect} Scion.  We hit him, and nothing seemed to work.  At best, we had knocked him off balance.



They hadn't seen me drop the bombs.  They hadn't been fully cognizant of what was going on with Scion expending power to view the future, or even that we were wearing him down on a level.  There \emph{was} a limit to how much damage he could sustain.



The saving grace had been the psychological impact they'd witnessed.  Scion \emph{hurting}.  Seeing his reaction to glimpsing the other being.



Maybe they didn't understand it.  Maybe they did.  But I suspected it was a factor in morale.  They'd seen a \emph{reaction}.



It was key, that reaction.



Now I was in an awkward position.  Unable to act, unable to access the specific capes I needed.  I had far, far more enemies than allies.  Beyond that fight from \emph{without}, I had to wage a war \emph{within}, struggling against my mind and body.



I was losing things.  I struggled to find a point of reference.



\emph{I'm a monster, }I thought.  Not an anchor, but a recent memory, a realization that was still fresh in my memory.  Something from just before I'd started losing memories.



\emph{Bullet ants.}



\emph{Maggots in eyeballs.  Necrotizing flesh.  Strip- stripping flesh from bone.}



\emph{Hand or knee?}



The images were so clear in my mind's eye that I could almost see them around me.  A hero in his civilian clothes, gasping for breath.  I had the means to save him, and I was holding back.



I heard a voice, female, kind words, spoken haltingly, out of place in the midst of this.  I had trouble placing the memory.



Then, more reassuring in a way, a return to the more violent thoughts.  \emph{Me standing over a man, pulling a trigger and watching the aftermath, bits of skull, brain and blood painting the pavement beneath him.}



\emph{The dance of bugs within a woman's lungs, minimizing the surface area available, limiting oxygen.}



A very different, very \emph{abstract} way of killing.



Again, the voice interrupted.  Patient, almost like I was overhearing something being said.  It made for a kind of\ldots what was the word?  A conflict between two ideas.  \emph{Dis- Dissonance}.



I tried to pick it apart, and in the doing, I realized what was happening.



With the loss of the portals, I'd lost one more anchor.  Pride, confidence, that reminder of who I'd been when I'd been a warlord, when I'd been at my most powerful, recent circumstances excepted\ldots I'd inadvertently connected thoughts and memories to that, and now that the physical manifestation was gone, those thoughts were disappearing with it.  My identity was degrading.



I couldn't be sure that anything I was reaching for was \emph{real}, or if I was taking something minor and exaggerating it in importance.



The Faerie Queen had been right.  If she hadn't warned me, if she hadn't told me I needed something to hold on to, I wasn't sure where I'd be right this instant.



I reached out, searching for other anchors.



The dog girl.  Her pet wolf had been changed into the alien `garden', and her view of it had been cut off when she'd retreated through a doorway.  She was staring at the empty space where the doorway had been.



Her teammate- \emph{my} teammate, had a phone out, and was talking and typing at the same time, while her eyes roved over the crowd.



She had only the two pairs of eyes, while I had limited, local omniscience.  We were each seeing the same thing through very different perspectives.  Unease, restlessness.



Here and there, people were breaking down.  Tears, panic.  The ones who had avoided the battle in the first place, the ones from distant Earths who had no conception of what was going on, the retirees.



Except they had support.  They weren't entirely alone.



I felt a measure of resentment.  I tried to dismiss it, but it didn't budge.



\emph{Alone.  A freak.  Crazy.  Broken.  Unhinged.}



I had no fucking \emph{time}, but I was paralyzed until \emph{someone else} made the first move.  If I stepped in now, I'd disturb the frail peace and tranquility that kept the group stable.  They'd rally against me.



I watched the monsters and the lunatics.  The tentacle girl was hanging back, hiding inside an apartment, trying to calm herself.  There was a cape from the Birdcage who was pacing.  When I'd picked him up, I dimly recalled, he'd been all alone, occupying one wing with two others.



I saw the trio of furies, on the fringes.  Pale, and somehow not even remotely human.  They reveled in chaos, and so long as \emph{one} lived, the others would come back.  Over and over.  As allies, they'd be useful, as enemies, they could and would deliver the critical, crippling blow that spoiled all our efforts.



The Faerie Queen was being very quiet and very still, but one of her puppets was tracking my location.  The most dangerous one of all.  Dangerous to all of us, not just \emph{me}.  I scarcely mattered at this point.



There was only the message I needed to communicate.  I'd seen it all, I'd seen what worked and what didn't.  I had an idea of what we needed to \emph{do}.



I bit my lip, hard, as if the pain could help me focus, bring me closer to being \emph{me}.



Watch, observe, wait.



Scion was killing the serpent-Endbringer\ldots \emph{Leviathan}.  Pummeling his chest, shattering it.  Cracks radiated from the wound, glowing gold.  Scion's face was twisted in fury, his fury was that of a berserker.  The blows were heavy enough that they drove Leviathan into the shattered earth below.  Water was flowing in around them, Leviathan's element, but the attack continued, the glowing wounds creating \emph{mountains} of steam around them.



Leviathan managed to get one fin to make contact with Scion, and the resulting disintegration created nearly as much mist, redoubling the effect.



The winged Endbringer advanced through the steam and golden-crimson mist, moving the one gun she still carried through the air until it was aimed at the two.



She fired, and it blasted a gust of wind at them, strong enough to push them and clear the wind.



The smallest Endbringer, flying in the air, unloaded a laser, three of its shadow pets' attacks and two more ranged powers on the golden man.  The resulting blast sent the ruined fragments of the settlement and the remains of the surrounding terrain spraying into the air.



The resulting crater that compared with the one Leviathan had made in the real Brockton Bay.



The blast had separated the two, leaving Leviathan hunched over, one arm intact and braced against the ground, head hanging, his chest peeled open.



Scion merely shifted his orientation in the air.  Not even shaking himself, not pausing to find his balance.  He was roaring, screaming, and in his thrashing movements, his blind fury, I nearly missed it.  In the moment he returned to an upright position, he flung out a sphere of golden light.



The light curved in the air, and punched into Leviathan's open chest cavity.



The Endbringer fell.  The color went out of Leviathan, his flesh breaking up, like clay overbaked in a kiln.  The fins were the first thing to crumble, the rest of his body following suit.



We'd \emph{taunted} him.  Teased him with the one thing he wanted most in the world, then we'd taken it away.



He turned his attention to the winged Endbringer and her smaller companion.  The towering Endbringer was already so damaged that she could only pull herself together.  The fat Endbringer was gone.



No, he was alive.  He'd created a time field around himself, and was healing in a more distant location.



Scion was doing too much damage to them.  They wouldn't win this fight for us.



No, it was the least of us, the smallest of us, which could have the biggest impact.  Capes I'd overlooked \emph{entirely}.



I blinked.  No, even more than that, individuals I was thinking of as useless, even now.



I knew what I had to do.



In the crowd, people were getting more outspoken.  Arguments had broken out.  Harsh words, criticisms.  Divisions were forming in the squads.  Almost all of them were divisions centered around certain individuals.  Virtually all of those individuals were ones who didn't play well with others.



It was a man in gold and black armor who stepped to the fore, a sultry looking woman following right behind him.  He shouted out, and his voice echoed, drawing attention from the majority of the crowd.



That would have to do.



With so little time to spare, I'd settle for a distraction.



One floor below me, a chute had been deployed.  Reaching twenty stories to the ground, it was arranged to let people on the upper floors evacuate quickly.  People would slide down, and the natural curve of the chute as it was pulled away from the building would keep them from being turned into a paste.



I used my relay bugs to extend my range, sent my swarm out, and then began securing it myself, tying the end to nearby architecture.  It was set up by the time we'd made our way inside the building and to the far end of the hall.



The faerie woman had noticed I was moving, but her attention was partially on the man in armor.  She was holding back.



I was preparing to go down with the clairvoyant, making sure we wouldn't break contact even if we had a hard landing, when I heard that voice again, small and afraid.



I couldn't place the recollection.



I couldn't use my flight pack with a passenger, so I made my way down the chute, and I hoped the material of the chute would hold.  I wasn't worried about the threads, thin as they were.  I knew spider thread.



It was nice, knowing \emph{something}, but I hesitated to claim it as an anchor.  It could be another misleading thing.



And if I ended up with one thing tying me to reality, I didn't want that one thing to be an obsession with bugs.



Images crossed my mind, possibilities.  If I still controlled \emph{people}, but I'd gone down some ugly path like that\ldots



I saw myself, haggard, thin, with minions in a similar state.  Eating bugs, wearing bugs and their materials, barely \emph{human}, my mind more like an insect's.



I focused on my friends instead.  Dog-girl and the girl with the phone.



They were moving my way.  Calling out to a girl who was getting her ruined hand stitched up by her partner.



The pair raised their heads, but they hesitated to follow.



A harsh word from the girl with the dogs got them into action.  It would have made \emph{me} move, and I didn't understand what it meant.



I'd reached the end of the ramp.  Perhaps not so gentle a landing as I'd hoped for, but it hadn't injured me.  I picked myself up and got moving in their direction.



I was losing track of who people were.  How were they supposed to be anchors when I couldn't remember who they are, or why they meant something to me?



I couldn't quite remember how she even knew I was coming.  I hadn't controlled her recently, and her power wasn't fresh in my mind.



It was with a measure of trepidation that I met up with them, the portal creator and clairvoyant following me.



Eerie, to be in such a large city with no people around us.



I could imagine how things would be if humanity was eliminated.  All of these ruined cities moldering, slowly crumbling\ldots



\emph{W-why did I find it com-comf- why did it re-re-reassure me?}



Dangerous, to think that way.



I was a tent in a strong wind, and the stakes were coming loose.  Only one or two remained.  Depending on the direction the wind was blowing when they were gone, someone could get hurt.



A tent surrounded by bugs.  Like this was a shitty camping trip.  I smiled a little at the thought, a broken giggle slipping through my lips.



\emph{N-no.  St-stay c-ccentered.}



The slur in my own thoughts made a chill run down across my back.  I pressed my hand to my head, as if I could \emph{physically} shift things back into place, or keep them from coming apart.



Again, that soft voice I couldn't place, something to help me keep moving onward, a human sound when abstracts were becoming all too real.



I realized the others were near, riding a dog.  The ones riding the stuffed lizard-Endbringer had stopped at the midway point, no doubt keeping watch.



The girl at the front flashed me a grin, raising a hand in a gesture I couldn't quite grasp.



She spoke, and I assumed it was a greeting.



I couldn't respond.  Didn't know how.  We were separated by a gulf.



She spoke as she spread her arms, raising her shoulders in an exaggerated set of movements.  Like talking louder to a person who didn't speak the language.  What was the fucking point?



She pointed at me, then in the direction of the crowd, then made the same movement.



\emph{The giant monsters are losing to Scion}, I thought.  \emph{He's coming, soon}.



I took her cue and started walking forward.  She hopped off the dog, \emph{scrambling }to get in my way, barring my path, her arms spread.



I stopped.



Her expression was \emph{stark}, rigid, wide eyed.  Her arms spread, she repeated the gesture a third time, arms and shoulders rising, then falling.



When I didn't respond, she spoke, her head cocked a little to one side.



I could hear the voice again.



Another person appeared twenty or so feet to my left, startling me.  My bugs moved, creating a barrier.



No.  She was a familiar face, so to speak.  A gray mask, horned, with mischievous eyes, a mouth hidden by a scarf or cowl  she'd piled around her shoulders.  She was the source of the voice.  She'd been with me, keeping me company.



Tears came unbidden to my eyes.



The blonde girl touched her cheek, pitching her voice high at the end.  A question?



The girl with the horned mask responded, gesturing in my direction.



I adjusted the clairvoyant's grip, then touched my cheek.  I was bleeding.  I had a gouge at the corner of my mouth, and my finger came away with blood on it.



Oh, I'd scratched myself, earlier.  I hadn't realized.  Hadn't meant to.



My hand shook as I stared down at it.



Alone, but not alone.  Isolated, but not isolated.



I needed to move, to go on.  Damn the consequences, damn whatever could happen to me.  If I could just get him to-



The dog girl spoke from her seat on the giant, monstrous dog's back.  Not a sentence, but a single word, clearly spoken to get my attention.



I raised my head to meet her eyes.  Her hair was shaggy, her gaze intense behind the mop of brown-red hair.



She held my gaze, silent, for long seconds.



Then she reached down, grabbing a loop of chain that was strapped to the dog's back.  She reared back until it looked like she was going to fall off, then heaved it forward.



It didn't fly \emph{that} far, but it landed partway between us, closer to her than to me.



I advanced, and the entire group collectively backed away.  Only the girl with the horns, behind me, advanced a little.



I reached down, the clairvoyant's hand on my arm, and I grabbed the chain.



I gave the chain to Doormaker.  He gripped it, and then he parted from me.



\emph{It's the ones I was dismissing entirely that are most important}, I thought.



I backed away, and she began reeling in the chain.  I walked him forward until he was out of my range, in their company instead of mine.



The dog girl didn't break eye contact.  She was watching me carefully.



She pointed at me, then at the sky.



No, not the sky, at bugs.



Me\ldots bugs?



Herself, then the dog.



Then at the portal man\ldots and, very slowly, taking her time, she pointed a door, as if unsure.



What did she mean?



Our respective powers?  Power?



She was asking about his power?



I didn't know about his power.  But it wasn't important.  I didn't care about his power.  It was secondary.  If they could fix it, it would help, but I doubted I'd be able to take control of people so easily.  Not a second time.



No.  I touched my hand to my mouth, then to my forehead.



I gestured towards him, then repeated the combination.



I drew a line with my bugs, pointing towards the crowd.



\emph{P-p-please on-unddersttand}.



The girl with the red-brown hair was nodding slowly.



She started to speak, but the blonde cut her off.  The blonde sounded annoyed, hurt, a little upset, but not in a bad way.  When she looked at me, her eyes were kind.  She brought the portal man to her and hooked one of her arms through his.



She understood, I was almost positive.  She cared, and I \emph{was} positive.  That annoyance, that hurt, it was only because she wanted to be the one who understood me and communicated with me, even in this rudimentary way.



I wasn't the only one who'd seen everything unfold.  The portal man had been there, linked to the clairvoyant through me.  He'd watched what I'd watched.  They could find a way to communicate with him, and they could get clues out of him, answers.



In the other Earth, the winged Endbringer fell from high above, her innumerable wings broken, ruined and bent.  She reached skyward, as if clutching for Scion, high above, and then the hand crumbled.



The rest of her followed suit.



The others were too broken to fight.



\emph{S-ssionns c-comminng.}



I was losing the ability to think in concrete words.  Needed- needed to get myself in a position where I could fight.



I took a step forward, and the others reacted.  This time, the auburn-haired girl had her dog move out of the way, off to one side.  The blonde didn't move.



In the distance, the faerie girl turned her head.  She'd noticed me move, somehow.



Why?



I knew what I was doing.  It was dangerous, yes, but so was Scion.



I almost stepped forward to control her, to move her out of the way myself.  Then I remembered that she was my anchor.  One of the few I had remaining.



What did I wind up as, if she was my only anchor?  If I could so readily envision myself as the bug-obsessed freak, lurking in dark places, what did I become with her?



Something close to human, at least?



She'd saved me, in a way.  I couldn't remember how, but I remembered that much.



I couldn't touch her.  I didn't even \emph{dare}.



She gestured with the\ldots \emph{phone}.  She started talking.  Not communicating in basics, but taking a shotgun approach, not stopping, trying everything, in the hopes that \emph{something} got through.



Scion stepped through into another world.  I'd covered our retreat in a fashion, but he was finding his way.



The moment he left Earth Gimel, the Simurgh scattered the mixed sand and dirt she'd gathered above her, then climbed to her feet, gun in hand.  The pieces of the fake body she'd formed of the materials at hand broke apart as they fell free.  She waited, recuperating.



It took seconds before he appeared in \emph{our} world.  The chaos was immediate.  People running, people moving forward to fight.



Glaistig Uaine cast one glance my way, then joined the fight.



It was time.



I picked up my phone, then used my bugs to carry it to her.  She gave me a strange look I couldn't interpret.



The bugs moved the string, and it tapped against her phone.



She typed something on my phone.  I brought it back to me.



I didn't understand the characters, but it looked like she'd done what I wanted.  The phone was set up to call her, when I needed to call her.



I could only hope that she understood when I started calling her.  She'd been reluctant to help before, hadn't she?  And now, when everything was on the line\ldots



I trusted her.



A noise made everyone's heads turn.  The man in gold and black armor had fired his weapon, and it had clipped a building.



Dust from the toppled building filled the street.



I moved.  I could see where my blonde friend was, where the others were.  I slipped by her in the chaos.



\emph{Ittt'sss ttimmme}.  My own voice was a buzz in my head, a medley of discordant sounds only barely resembling words.



Time to fight, gathering my forces.  Not an army this time.



I broke into a run, best as I was able.  Where my own feet failed me, my flight pack kept me aloft.



I could see \emph{everyone}, even in the dust.  The clairvoyant let me see as if I was looking from every perspective, everywhere.  It was easy to collect the first few I encountered.



The girl with the mangled hand and her partner, riding the stuffed lizard.



A sharp right.  Moving around the perimeter of the flight.  The faerie was busy fighting, but if she saw an opportunity, there was a good chance she'd kill me.



There were others, but I was having trouble keeping track.  I knew them by their powers.  Brutes, hanging back.  Tough enough to weather most fights, but barely capable of holding up against \emph{Scion}.



That took a special kind of toughness.



A woman covered in a skin of forcefields, protecting people with massive shards of forcefield.



I passed them, making a beeline for someone else, flying over the cloud of dust, trying to see people.  She'd been doing rescue before, getting people to where they could be helped.



Now\ldots now she was a tool I needed if I was going to win this.  We climbed onto the stuffed lizard's back.  I bound the clairvoyant's hand to mine, mindful of the damage that had been done last time.



The stuffed animal climbed up the side of a ruined building.  With the clairvoyant's hand and feet and my own flight pack, we dismounted when we reached an opening large enough to hop through.



The girl with the ruined hand shifted position, slumping over.  They climbed up to the highest point they could reach, and then the girl who controlled the stuffed humanoid lizard called out, incoherent.



I couldn't get her to talk properly.



So I had her wail instead, a frantic sound that was \emph{justifiable} in how little sense it made.



A girl with flying armor and bright yellow hair descended, ready to help the apparently wounded girl.



When she got close enough to touch them, she fell within my power's range.



I brought her to me, the movements shaky and unfamiliar.  Easier on autopilot, but I didn't have time to wait for her to drift my way.  Movements of the feet controlled movement direction and altitude.  I brought her to me.



Then I made her sing.



\emph{Th-thin-think ab-abbboutt cc-courrrage.  Aabbout m-mmovving fforrwarrd.}



I could only hope the song conveyed the right meaning, the right impulse.



I pressed the biggest blue button to call my teammate with the number she'd set into the phone.



It shifted to a video call.  I saw her on the other side.



How to even explain?  To convey the next step?



I used my bugs to illustrate.  A mass at the center, pulses traveling to other nodes.  To \emph{every} other node.



She said something.



A minute passed.



Something hit the ground hard enough that the building \emph{swayed}.  Not merely a shaking, but a side-to-side wobble that suggested that anything harder might see the entire thing tip over.



And the song began playing, echoing, through three other phones in my immediate vicinity.  Two held by the ones who'd been on the stuffed animal, and a third-



I was distracted before I could look for the source.  My clairvoyance told me there wasn't anyone nearby.



All through the battlefield, Protectorate members and Wards had phones playing the song.  It gave them strength, courage at a moment they felt weak.



A woman I recognized from Brockton Bay threw the phone aside, then shot it with a shotgun, before changing the gun to something else and opening fire on Scion.  It took the man in gold and black armor a second to get a chance to do the same.  One of his underlings, a cape who was named after a siege weapon, took his boss' lead.



It served as something to urge people onward, to focus them on one target.  But those three, or those \emph{two} were savvy enough to know something could be up.



We moved.  The armored girl with yellow hair helping to hold the clairvoyant while I descended to the ground with my flight pack.



The movements of the other two weren't coordinated well with my own movements.  They rode the stuffed animal as it leaped to the next building, but momentarily passed out of my control.



They didn't turn on me, didn't shoot me.  They carried onward, and I adjusted my course to put them in my range again.



I got the one-horned woman who glittered with forcefields, then changed direction.



The next group was harder.  They had advance warning we were coming, shared by a brown haired girl who wore a black dress and no mask.



I felt a pang of emotion.  I couldn't even put a name to it.



The girl rattled off words, \emph{numbers, }in response to questions asked by a woman with body armor and a bristling ponytail.  Monstrous capes moved to flank her, protecting her.



Every second counted.



Couldn't give the precog a chance to get hard numbers.  With every moment that passed, every loping movement of the stuffed lizard that followed beneath me, the pair exchanged question and answer.



I was a threat.  I was being reduced to numbers.  Success, failure.  Nothing more.



Which was all this really was.  Only I was focused on success and failure on a much bigger scale than this confrontation.



The forcefield woman sandwiched each of us between two forcefields, then \emph{willed} them forwards.  We left the stuffed lizard behind.



Three more questions, rapid fire.  One word each, \emph{names}.  The woman with the mask only heard the first syllable of each response before moving on to the next.



She gave a command, an order, and a red haired woman in a black skintight outfit turned, aiming her gun at a wall.



The bullet ricocheted off the wall and flew right through our group.  My forcefield woman went down, and the crystals we were riding fractured, coming apart enough that we fell to the ground.



Only the string tying me to the clairvoyant kept us together.



A fat, bald man stepped forward, blocking my way with his body.  A young man with orange skin, a tail and bright pink hair did the same.



But the young precog said something, and stepped forward as they parted to give her room.



She spoke, one word.  My name.  I was pretty sure.  What was my name?  did it start with a `T' sound?  An `S'?  A `W'?



An `M'?



``Murrruuh-hurrrrrrrrh,'' I managed.  I slowly pulled myself to my feet, my movements jerky, shaky.  Worse than it had been yet.



\emph{Y-youuu ss-set mme onnnnn th-thi-this roadddd.}\emph{Y-youuu oh-owe mme thhhhhisss.   Ddd-dohnn't gg-get-t innn myy w-wayyy n-noww.}



Scion toppled a building.  Capes erected barriers to protect a whole \emph{squad, }over a hundred capes, but the building disintegrated on impact, rubble pouring off the barrier like water off a roof, crushing the people who didn't have adequate shelter.



She didn't move, staring at me.



I had the clairvoyant reach into my belt.  She withdrew a scrap of paper.



My bugs carried it to the young precog.



An I.O.U., if there ever was one.



She stared down at the two and a half words, then crumpled it.  Her head hung.



Before any of the others could stop her, she stepped forward, into my range.



I pushed her \emph{out}, the movement forceful enough she stumbled a bit.  The fat one caught her.



I pointed.



The group parted, giving me a view of their other members.



In the distance, Scion was struck, knocked into a building.  The work of the man with the giant sword.  The faerie readied to follow up, then hesitated.



She flew my way instead.



No time for grace or decorum.



The woman with the forcefield scales used her power.  Another sandwich of crystalline fields, the more secure way to hold someone, and she hauled the reality-warper out of the other group, into my range.  Another forcefield caught a boy with glowing hair.



The remainder dropped into fighting stances, a gun was trained on me-



And the precog cried out.  One word.  Negation.



They stopped in their tracks.



I turned to go, my recruits in hand.  The faerie girl was coming.



I didn't fight.  I had the key components.  The trick was to set everything in motion.



I accessed the power of the reality warper.  The girl who got more powerful as she lost touch with the world, who could fashion her own realities, then bring them into our world.



I had her create a door, then I used her partner's help to smash it.



A freestanding hole in reality.  The reality warper used her power to pick a world.



I wasn't too picky.  The instant I was through, I had them make two more.



Then two more.



I protected them all with forcefields.



I didn't have the portal man, but I did have this as a means of traveling \emph{sideways}, like Scion could travel in this direction that wasn't up or down, left, right, forward or back.



It didn't let me cross all the way into other continents.  Movement was \emph{analogous.}



Still, it made ambushing other groups easier.  I could use the clairvoyant to see where we were in analogue to the other world, then smash a doorway open, putting me right next to whoever I wanted.  The song helped keep them focused on Scion, kept people from running.  It wasn't perfect, absolute control, but it was a means of keeping us all together.



Scion hadn't done much planning for this eventuality.  For a world where \emph{everyone} was against him.  In every world I'd glimpsed, we were fractured, whole nations worth of good capes hanging back or fighting with the others.  He'd hidden the strategies from us, but I could connect the dots.



It was about keeping him off guard, putting him on unfamiliar footing.



I could only hope that \emph{everyone} was enough people, right now.



I found the boy who made hands and faces out of surrounding materials.  A teammate, a friend.\emph{  }He'd worked with me on something important.



I put myself right in the middle of the group, collected him, and then left.



When others moved to follow, I set another forcefield up, and retreated through a series of doors, leaving decoy doorways in my wake.



The power booster, to give myself more control, and to enhance the song.  To enhance the reality warper and everyone else I'd chosen.



The girl who made her dreams into projections.



The boy, her ex-friend, who could turn anything into a bullet.



And then the man who could \emph{connect} things, so the movement of one would move the other.  I stepped through, and he was ready for me.  He moved a short iron rod, and the partner rod caught me by the neck, pinning me to a wall.



His partner dismissed the illusion.  A displacement effect that made them appear to be where they weren't.



The \emph{connection} man was more dangerous than he seemed.  The rod that was pinning me would keep moving to the side if he kept moving his own rod.  Even if there was stuff in the way.  It might distort or break, but he wouldn't feel any resistance on his end.



My \emph{throat} would probably break apart before the rod did.



He spoke in broken English.  Still more capable of speech than I was.



I had the others behind me.  The forcefield woman made a field behind him.  He blocked it with another pair of rods that whipped up from the ground, connected to something in his sleeve.



The telekinetic girl with the stuffed animals used threads, binding him.  Another means of pulling him closer.



A moment later, his cloak went rigid, fixing him to the ground.  Other threads still bound his flesh, biting deep enough they threatened to draw blood.



His partner used a power, and the threads moved five or six feet to the left.  They recoiled to the telekinetic's grasp.  He backed away a step, keeping his distance from me, extending the connection between the rods so it stayed against my throat.



The movement of things to one side wasn't an illusion, or it wasn't illusion \emph{only}.  Selective space redistribution, probably usable on \emph{light}.



He pressed me harder against the wall, speaking in a low, grave voice.



If I could have \emph{asked}, I would have asked.



All at once, he staggered, and the pressure on my throat let up.



A girl with a horned mask had appeared beside him, pulling his robe up around his head.  She dragged him forward staggering, and heaved him into my range.



A moment later, she was gone.



I had all of the \emph{individuals} I needed, though I had a hunch about another I'd left behind.



I found one of the larger groups, then moved my army into position.  A group of select individuals, to give me the powers I needed access to, all falling within sixteen feet of me.



I formed the doorway, then broke it open.  The final piece, for the time being.  It was a group I'd initially dismissed, a group that had sat out on the battle.  Now they came into play.



\emph{Changers.}



Capes who could change their form, capes who could take on the faces of others.  The clairvoyant and I dropped from a portal in the air and landed right in their midst.  Crystalline forcefields appeared in the air, then lowered slowly enough that people had a chance to get out of the way.



I picked the faces of every changer in my range, watching to make sure it was accurate.



I couldn't control them while they were outside of my range, so I'd do something cruder, instead.



I chose their faces, and then I seated them on the crystalline forcefields, binding them in place with the connection man.



I scattered them into the sky.  Each one rooted to a forcefield platform.



Then I tapped the reality warper's power.  I began shaping a world.



I could see my blonde friend with the portal man, talking to people.  Talking to\ldots what was his name?  The one who gave thinker powers.  \emph{Teacher}.



He'd given the portal man the ability to talk.



A power I was afraid of taking for myself.  Because I couldn't lose even an iota of willpower if I was going to make it through this.  Because I couldn't fall into his grasp.  Because I was afraid of finding out that even \emph{he} couldn't help me.



The portal man would explain what he'd seen.  With luck, my brilliant friend would be able to connect the dots.



The reality warper's world was shaped.  Crude, but I could use the same piece over and over again.



A landscape of body parts, of hands and limbs, of faces.



I used my friend, the young man who could create hands and faces.



I began altering the city.



Scion was in the midst of fighting a monstrous, hulking dragon-man and the warlord with the death-eating shadow.  He saw the first of the faces that the reality-manipulator had created and lashed out, demolishing it.



The dragon-man took advantage of the opening to burn him.



\emph{Hhhe\ldots nno f-filtttterrrs.  Hhhhhisss emmmotions\ldots rrrraww.}



Scion fought his way free, and the warlord went on the offensive, lashing out.  She'd collected the bodies of the dead, as the faerie girl had collected their `spirits'.  She was strong, though not quite as strong as she would have been if things hadn't gone sour.



He tore into h- her pet and the damage was permanent.  She pressed forward anyways, forcing him to retreat above the skyline.



He came face to face with the changers.  Wearing his companion's face.  The face of the alabaster-skinned companion my friends had put together, other faces like them.  Companions that \emph{could be}.  One metal-skinned boy I'd salvaged from the ruins of a recent fight had been molded into a steel-skinned companion.  Another was a female mirror of Scion himself, golden skinned.



He moved to strike out, and I hurried to get them out of the way, using the connections and the forcefields to move them to the safest places I could find.



Some were catching on, changing back.  Others weren't so quick in their ability to change.



This wasn't an attack on his body.



I was going after his mind, his emotions.



If the feelings were still raw after thirty years, if he hadn't learned how to handle it, then I'd target that as his weak point.



\emph{Sstrennggtthhth wwwwee h-have\ldots y-yy-you ddo nottt\ldots  w-we d-dealll\ldots with-thth l-lotsss\ldots painnn inn-n\ldots ou-ouhhrr livv-ves.}



Remind him of what he didn't have.  His partner, his\ldots life cycle.



Hands of stone emerged from around the city.  More of reality warped around us.  When she'd changed everything in her range into a simulation of the `garden', I turned it into a portal, changed the chan-chann- station to something where it was all solid.  Rock, ice, dirt.



Then I moved her somewhere else, and started over.



All around Scion, piece by piece, the world was changing.



So much, so fast\ldots it wasn't all on my end.



\emph{Mm-m- my ff-frrriennndsss.}



They'd connected the dots.  They saw what I was doing and they were getting others on board.  Illusions crafted of smoke.  A space warper who could mold buildings was making faces.



Maybe they even saw my end goal.



My feelings swelled, and the faint singing that was echoing through the various phones seemed to mimic that.  Was that my control being reflected through her?  Or was it something on her end?



He was reacting.  Spending as much time destroying the landscape as he was on \emph{us}.



It was a sh-shift in our favor, and he was getting more agitated with every passing second.



We were approaching a critical point.



I pulled the changers back, and I moved to the location of some masters instead.



Projection capes.  Only a few.  But it helped.  I had the girl who made dreams into projections, and a clone-hybrid of two of the killers, capable of making poisonous, noxious illusions out of the landscape.



I put her power to work, showing her what to do, then sending her to work, beyond my range.



The song helped.  The song meant that when I \emph{pushed}, they kept moving.



By the time the impulse and momentum wore off, they were well on their way, and I was gone.



\emph{Nn-neckxt\ldots n-nexttt.}



I took a step, and my leg gave way.



I tried to stand, and it failed me again.



The ones I controlled helped me to my feet.  I leaned on them as they supported me.



\emph{Neh-next}, I thought, again.



My body was failing on me.



A part of me had hoped that when this was all over, I'd be able to retreat somewhere.  I \emph{knew} I'd have enemies, that there was no way I could show my face again.



I could, I was pretty sure, get by with a good stockpile of books, a place in the middle of nowhere.  Not \emph{cold}, but maybe a place in the mountains or on some island.  Retreat from the world.



Then it had taken reading from me.



It had taken my ability to understand language.



My ability to express it.



Now it took my body.



My mind was sure to follow.



The projections began to haunt him.  They emerged from walls or crept around corners.  Images of his deceased, slain partner.  Images of others, which almost seemed to bother him \emph{more}.



If he was forming any kind of tolerance, it was slow.  He wasn't getting a chance to \emph{breathe}.



Scion was striking down these constructions faster than I could raise them.



Up until the moment the man in gold and black armor shot his sword at him.  It bought time to put more of these illusions and constructions in place.



Scion righted himself, then hesitated.



Fury was giving way to a kind of \emph{fear}.



I knew this fear well.  It was a fear that was all too easy to fall into when one's focus was too narrow.  To be caught up in an environment, facing down a relentless torrent of negative experiences.  Even the minor things added up, if you couldn't step back to look at things in perspective.



He fought back.  That was a fairly normal thing.  A lot of people fought back when they faced something like this.  A lot of people liked to think they could fight back up until it stopped.



I limped forward, my squad in step around me, filling my power's radius.



Those types of people tended to underestimate the tenacity of the well and truly \emph{fucked up }individuals of this world.



It was lowly, to turn to \emph{this}, but I'd never pretended to be honorable, above any of that.  When shit was on the line, I'd go as far as I had to.



I had the reality warper create another doorway.  Her buddy knocked it open, and she tuned it back to our original er-



Ear-



\emph{Earth.}



The stuttering thoughts paralyzed me for a moment.  I floated up a bit to see over the rank and file of my swarm, the clairvoyant holding on to my leg.



My friends glanced up at me.  I barely recognized them.



I pointed at the portal.



There was a short, fierce discussion.



I felt my heartbeat pick up.  Why weren't they running?



Scion was going to \emph{snap}.  He was going to destroy\emph{ ev-everything}.



But my friend was talking into her phone.



Scion was getting more frantic, a mix of fear and rage.



\emph{Panic?}



Scope, scale, he was no longer reasonable about what was going on.



If he'd been holding back so he could leave \emph{some} of us alive, in the chance that another companion would show up and he would be able to resume his normal life cycle, then I was suspicious he was about to \emph{stop}.



And my friend continued talking into the phone, a stern expression on her face.  She was tense.



I tried to turn the clairvoyant on the scene, but the view was so narrow now, I wasn't really able to see more than I could with my own eyes.  I could choose where I saw \emph{from}, but that didn't help me evaluate the crowd.



I could see the Endbringer arrive.  I'd opened a portal to Gimel in the process of making mouseholes between worlds, and she was the only one that remained.



She sang, a shrill song that echoed in every mind I controlled, her song joining the one that echoed from the phones on belts and in pockets.



Then she began shaping the environment.  Clouds of dust took on shapes, looming over Scion.



Everywhere he turned, he faced reminders of what he'd lost, of a loss he couldn't figure out how to handle.



H-he was a member of a species that had won for however many cycles, utterly bewildered when we \emph{drowned} it in its defeat.



The winged Endbringer's attack was the straw that broke the camel's back.  He was hunched over in the air, hands on his head, knees against his chest, rotating as though gravity didn't touch him, no conception of up, down, left or right.



He was \emph{shaking}.



\emph{Any second.}



A slit of light appeared on the battlefield.  It yawned open.



Others began to follow.



\emph{T-theyyyy fixxedd himmm.}



Except it wasn't him.



It was the faerie girl.  She had him as a shadow-puppet.  A ghost.



I could hear my friend swear.  The others around her were tense.



They turned to run, sprinting through the portal.



Thousands of doorways.  She turned and looked in my direction.



But nothing appeared nearby.



The faerie girl was opening doorways for everyone \emph{but us}.  Everyone but \emph{me}.  People were running, fleeing into other worlds, and we were being left on our own.



I couldn't \emph{cc-cllose} the portals I'd made with the reality warper.



We ran, or the others ran, and I was mostly \emph{carried.}  We entered one world, then ducked into another door I'd left nearby.  We zig-zagged between universes, using \emph{realities} as cover.



There was no \emph{sound}.



No scream, no explosion.



It was a scouring light, no direction, no aim, nothing held back.



The initial shockwave passed through doors, and it \emph{expanded} in every direction with each door it passed through, sweeping past everything within ten miles of each portal.



The moment we were through the last portal, I'd connected every member of the group to a forcefield.  The forcefield was then \emph{flung} forward, carrying us with it.



Eased to a stop when we were out of range.



When the light faded, there was only flatness and portals.



I moved my hand to point, and my hand couldn't make the gesture.  My fingers refused to extend independently.  I could see the hesitation on the faces of the others.



But I could \emph{see}.  I could see what was going on.  I led my squad forward, and the rest followed.



I found the faerie queen, in the center of the group of rescued.  Portals stood in concentric circles, with gaps so they could be navigated through.  A stonehenge of glowing doorways.



I walked, stopping in the middle of an open field.  I watched.



I saw Scion, just barely recovering.



I saw the faerie girl, talking to others.



I watched, and long seconds passed.  Others around me were talking, just beyond my range.  There was a voice in my ear, coaxing, asking questions.



She banished two spirits, keeping the portal man.  Picked two others.



I didn't wait for them to fully materialize.  I created a doorway with the reality-warper and kicked it open.



I appeared right behind the faerie queen.



I seized her, and I seized the portal man she'd killed and claimed for herself.



I opened a doorway to Scion, and I unfolded a cloak of portals, capturing people.



I found the tinkers I'd left on the other earth.



When we emerged, he didn't react.  He was lost in his own mind.



The dream-projector fell unconscious, and was captured by her onetime friend.  A glimmering of the garden-entity.



It loomed, rising into the air before Scion.



He recoiled, striking at it.



My \emph{swarm}, feeble as it was, formed a reaching hand.  He struck at that, in turn.  The impact wasn't as strong.  A distraction, maintaining pressure, nothing more.



I opened a doorway, and I found one individual I'd left behind.



The boy with the changing faces.



The number man had said he'd taken a dose that had been focused on helping the entities be \emph{human}.



I couldn't change his face \emph{intentionally}.



As it turned out, I didn't have to.



I could \emph{feel} Scion's reaction, through my senses and the individuals I controlled.



Hope.  For just a second.  Not even the faint hope he'd experienced with the fake my teammates had put together.



Because somehow, this boy registered as being like this entity's companion had been.  Registering as the same state, as the power that made it so similar.



In the moment that hope died, the girl with the injured hand used her power on the iron rods.  Infused them with the energy he was afraid of.



Those rods became projectiles, in another's hands.



His hope was gone, he was bewildered, scared.



He didn't try to dodge.  He couldn't or wouldn't.



They impaled him.  One in the head, one in the chest.



The tinkers fired their weapon.  An interdimensional ram turned into a gun.  They'd finished it while they weren't under my control.  \emph{Defiant} was the one ready at the switch.



I discovered why he was concerned about the power.



It kept things from being \emph{contained}.  I got a glimpse, a flash of a look into the world beyond him, a world he'd shut off, to which his body was the only conduit.



The beam tore into him and into the well.



I moved the portals, and the beam turned to scour more of the landscape beyond Scion.



The Faerie Queen began to slip from my grasp.



She knew what was happening, and she was forcing my power to affect her spirits.  A single spirit.



Breaking free.



She moved her hand of her own volition.



And then she was free.  Inside my radius, but free.



She turned to face me.  I met her gaze, as best as I was able.  My vision wavered.



Her head hung.  She made no move to resist.  She didn't close the portals.



More projectiles, opening more doors.



The beam ran out of power.



The dead remains of the entity showered the ground at the center of the wasteland.



I staggered.  The emotion around me was too much.  I pushed people away, and they bumped into one another.  Some left my range, only a handful remained.  I didn't recognize a single one.  Even the one holding my hand.



I couldn't shake the feeling I'd somehow betrayed myself, and I wasn't even sure who \emph{I} was.



It was over.  And I was free to finally lose my mind.





