





I was plunged into darkness.  Things stopped making sense.



I was surrounded.  I couldn't think straight because I couldn't \emph{think}.  Trying to analyze people, to parse them, to identify them, it was like being in quicksand.  Resistance to my efforts, getting nowhere, and always slowly, inevitably sinking.



Thirty, forty, fifty people, more appearing every second, streamed through portals.  All of the survivors, returning to the battlefield to see it for themselves.  To turn their eyes towards \emph{me}, because the only open space in the area was the space around \emph{me}, the radius of my power, and it drew the eye.  People noticed, and others paid attention to the \emph{noticing}.



The looks were hostile.  All the worse because they \emph{were alien}.  Hundreds of people, and they didn't feel any goodwill towards me.



Strangers.  Not strangers like people I didn't \emph{know. } That was different.  Strangers who had \emph{connections} to me, who I \emph{still} didn't know.  Strangers like the masked man who broke into a house.  Strangers in the sense of a stalker.  Of a jury about to announce a sentence.



This darkness around me, it was an absence of illumination, an absence of any light that could clarify and make sense of things.  I couldn't recognize anyone, put a finger on them as familiar or unfamiliar, enemy or ally.



This\ldots it was all ominous, vaguely threatening.  People I might pass on the street wouldn't pay me any mind.  People \emph{here,} almost every single one of them, they had a reason to pay attention to me, and the attention wasn't \emph{good} attention.



Any of them, \emph{all} of them, they could attack me at a moment's notice.  Inflict horrible tortures, kill me, fates worse than death.  There were a \emph{lot} of fates worse than death.



I was settling into the end-state of my transition.  I knew it, and I could see the dividing lines more clearly.  What I could still do, what I couldn't.



Taking action, moving\ldots easier so long as I had an objective.



Objectives, too, were easier.  I could still analyze.  I could survey the battlefield, interpret powers, put two and two together.  I could connect the dots, recall the powers I was up against, and I could form strategies.



My head hung, but I could see the eyes of the people around me through the clairvoyant.  They fixed their stares on me, and I could feel paranoia building.  A weight, a \emph{pressure}, crushing me from all sides.



I couldn't recognize anyone, only powers.  Everyone was a potential enemy.



Everyone was capable of using their powers to hurt me.



Damn them all.  After everything I'd done, everything I'd \emph{given up}, and they were standing there, \emph{threatening} me.



Not a word was spoken, though the singing continued in the background.  It conveyed the story to those who were still arriving.  There were only two reasons things would be so still.  The first was that battle could be utterly lost and there was no more need for orders, for communication, for cries of grief and screams of pain.  That there was nothing left but surrender for the ones who remained.



But this wasn't that, I had to remind myself.  We had \emph{won}.  That disbelief rocked each and every one of the people who were present, that silence marked a kind of respect for the fallen.



And, all too possible, it marked a kind of unspoken agreement.  I could see it.  The silence was a relief and an added pressure, giving more weight to the eyes on me.  Every pair of eyes was telling me the same thing.



I was the next big threat.  The next one that had to be killed before this could all \emph{end}.



I tensed.  I could barely move, but I could still ready myself for a fight or flight response.  Maybe I wouldn't be able to stand, but I could use the device on my back, I could throw myself at the first opponent to approach me.



I was lost in this special kind of darkness, but I could analyze this situation too.  I could look at my capabilities and what my power had taken away, and I knew that there was a common theme at work.



\emph{Con- conflict.  }I could function so long as there was conflict, so long as I was creating it or resolving it.  Given the choice between paralysis and conflict, I wondered if anyone would really choose the former, committing to it over time.



Paralysis was a scary thing.  There were a lot of forms of it, and they ranked up there as far as fates worse than death.



Conflict was better.  Familiar.



My swarm informed me that I still had my knife, tiny legs tracing over the weapon's grip.



One tinker came through a doorway, as if to survey the situation.  Heavy armored boots \emph{rang} as they struck the glassy, blasted disaster area.  The man emerged, and he cast a glance around.  He took in, no doubt, the ruined buildings, the clouds of dust that were rolling \emph{into} the clearing, still following the vast amounts of air that had crashed into the space to replace the atmosphere the blast had wiped out.



The tinker pointed his weapon.  The rest of the tinkers filed into this world, two by two.



Everyone, just about, was making their way here.  Thousands, now.



Strangers.  All of them would, circumstances demanding, aim to get in my way, to stop me, question my actions, \emph{condemn} me, hate me, maim, torture or kill me.  I'd seen good people go bad, couldn't trust anyone.



My memories were incoherent, but I could see the common themes, and I knew everything they could and would do, given the chance.  Pyrokinetics could burn, telekinetics crush.  They weren't the scary ones, as painful as a burn or other injury could be.  It was the thinkers that worried me, the masters, the \emph{tinkers}.



I watched that crowd with one eye.



Some of them would kill me the second they thought they could get away with it.  Others would be scheming.  I had power, they wanted that power for themselves.  They'd take it like my portal man was taken from me.  They'd take \emph{all} of it.



My hand was clenched so hard I thought something might break.



Had to remain still.  I had a handful of soldiers, a swarm of sixteen people who\ldots



I'd pushed them away, and these were the ones who I hadn't pushed \emph{out}.  Why had I pushed them?



Had I already been interfered with?  Had someone already made a move, manipulating me?



\emph{Rrreee-}



I shook my head a little.  Couldn't form complete thoughts.  I felt a light weight on my shoulders, heard a voice.  Reassuring, coaxing.



So very small, compared to everything I was seeing, everything I was up against.  The voice did nothing for me.



I was prey in the sights of a predator.  Frozen.  When two snipers fought, the one who shot first was at a disadvantage.  The other would see the muzzle flash and be on target.  It was the same for me.  My enemy would see the direction I was moving, the strategy I was putting to use, and they'd intercept me on both fronts.



Being small and still helped.  I wanted to cover myself, to hide in my swarm, big or little, but I couldn't afford to move.



Again, the voice.  I shifted the clairvoyant's grip, sliding it up from my wrist to my shoulder.  Severing threads so the hand was free to move.  Once it was on my shoulder, I moved it under a strap and used the cut threads to secure it in place.



My hand was free.



That singing-  Singing was \emph{bad}.



But it wasn't the- wasn't the winged being that was perched on a building at the far end of the battlefield.  She was silent, her wings folded over her shoulders and along the edge of the rooftop.  Worse for wear, with wings broken, but her body was pristine alabaster, her hair blowing in the wind.



The singing\ldots it was one of my minions.  The words had been faster in tempo before, now they were\ldots I wasn't even sure.



Singing was \emph{bad}, wasn't it?



I silenced her.



Stunning, to be in the middle of a city and not hear the roar of distant traffic, of conversation or anything of the sort.  There was barely any wind, even, and no debris here for the wind to stir.



There was only my swarm.  A dull buzzing roar in my ears, for the smallest ones.  I could sense the pounding heartbeats, feel the breathing.  I could imagine the sounds so clearly that I couldn't pick it apart from what I was actually hearing.  Periodically, I could hear a voice, which was the same in some ways.  In my head or in my ears?



Muscles \emph{creaked} when moving.  For some, bones \emph{ground together}\emph{.  }Joints popped.  Stomachs gurgled.



My swarm had formed a loose ring around me, more by accident or manipulation than by any \emph{design} on my part.  There was a gap just beyond them, where others were afraid to cross.  The noises of their bodies, the sensations, the perceptions\ldots they were an island of forced familiarity in a sea of hostility.



If even one \emph{wave} of that sea hit me and my island\ldots if they charged, if someone gave them an excuse\ldots



I repositioned my hand, a shaky, uneven movement.  One side of my wrist pressed against the butt-end of my knife.



The last of the phones finished relaying the music.  Only two seconds had passed?  If that.  The spell broke.



Someone cried out.



It had started.



The outcry was picked up by others.  People grabbed one another, arms were thrown around necks, fingers dug into costumes and skin.  They whimpered, screamed, shouted.  I could see tears in eyes, faces contorted in emotion.  Groups turned inward, focusing on one another, loners backed away, positioning themselves where they had space to maneuver.  Madness, hysterical, chaotic.  Grown adult and child alike, costumed and uncostumed, individuals dressed in white or in bright colors, individuals in black, they were part of the riot.



They held nothing back, emotionally.  I saw fireballs explode in midair.  People streaked into the sky, lightshows following after them.



But the yelling, the echoes of that first cry, they were what shook me, what shook \emph{everything}.  The only thing around us to block the sounds were people, and those people were making \emph{more} sound.  Thousands echoing of that one cry.



None of this surprised me, that they'd turn on each other the moment the real threat was gone.  It was the way our species operated.  A reality that had been writ over and over again in my experiences.  I couldn't remember the specific cases, but the lessons remained with me.



I was standing, already, making my way to my feet with the help of the clairvoyant, with the device on my back, the attached arms.



Easier to move when there was something to do.  Fighting, fighting \emph{back}.



My movement had drawn attention.  I started to draw my knife, and something stopped me, keeping it in its sheath.  I abandoned it, turning instead to my swarm.  They shifted positions, ready to use powers, to protect me against outside threats, and my bugs filled the spaces between them.  The strangers around me responded in kind, preparing for a fight.  Thirty, fifty people, waiting for me to act.  More lurked in the fringes, ready to step in.



It wasn't an unfamiliar experience, to be surrounded in chaos, to be arrayed against impossible odds.  For what I was now, for what \emph{remained}, it felt only natural.  All of this was as I'd expected.



They were talking, exchanging hurried words, questions.  Trying to cobble together a strategy.  I had no such need.  \emph{My} side didn't need to communicate.  They were perfectly coordinated.



Everyone here was a potential enemy, and I'd treat them appropriately.  I just needed to focus, to get my bearings, and identify the biggest threats to me.  If I eliminated or captured them, I could systematically kill everyone present.



It was\ldots not a calming idea.  But it reassured.



I was just a little unhinged, my perceptions were broken.  I knew that.  But if I had to live like this \emph{forever}, if everyone was a threat for the rest of my life, I'd well and truly lose it.  Stopping them, eliminating them and bringing them under my control\ldots



The only way we'd all achieve anything resembling \emph{peace}.



I'd wanted peace for a very, \emph{very} long time now.



After everything I'd given up, I deserved peace.



Someone was pushing their way through the crowd around me.  I tensed.  My hand went to my knife again, and again it was stopped.



I heard the voice in my ear.  It was \emph{trying } to sound soothing, gentle, but it was failing.  I heard the fear in it.  That fear was reassuring in its own way.  It told me I was right.  That the world \emph{did} revolve around fear and violence. That I was doing the right thing, standing guard, being ready for a fight at any moment.



The madness around me continued unabated, the shouting fading, then starting anew, picked up by others, different factions, fresh sets of lungs.



I wasn't going to listen to the voice. Not with all of the powers arrayed against me.  it would be idiotic and foolish if I did listen, whether I understood or not.



The others, they were arguing amongst themselves, barking out insults, yelling, pointing at me.  I'd taken control of them, and that was a \emph{fresh} wound.



The individual reached the edge of the crowd.  A man, bearded, with a small entourage of people wearing white.



When he spoke, his voice was soothing, a constant stream of words, more like he was talking to a wounded animal than a person.  He stopped at the circle's edge, and I could see how many of the others were tense, wary.



They recognized him, and they didn't like him.



If I was going to exterminate them all, then I could use the fact that they weren't all friends.  Let them fight each other, wear each other down\ldots



Except I had \emph{this} to focus on first.



He was gesturing at his mouth, moving his hand as he talked.  he pointed to me, then to one of his underlings.  He repeated the three gestures, speech, me, underling.



I wasn't stupid.  I grasped his meaning.  I could see others around the circle relaxing.



But they weren't relaxing \emph{entirely}.  But they were relaxing, tension leaving their shoulders and hands.  Weapons, poised at the ready, dropped a fraction.



He was saying he had a means of communicating with me?  But it, or \emph{he, }couldn't be trusted a hundred percent, judging by my own gut and the reactions of the others.



He sent one of his underlings into my reach.  A boy with a shaved head and thick eyebrows.



I felt the underling's body and powers unfold before me, and I could tell right away that there was something wrong.



My eyes told me one thing, my power told me another.



My eyes told me the man was just beyond the reach of my power, the boy following his orders.



My \emph{power} told me that whatever the boy looked like, he was a half-foot taller, he had a beard, and he was loaded down with trinkets and tidbits.  I recognized him by his power.  He made thinkers and tinkers, granted powers.



He had three more, hanging back, watching.  No doubt to help facilitate this ruse, whatever it was.  To watch for people who could see through it, to watch his back.



He was putting himself in my power.  Whatever he'd had his other self, his disguised underling or his clone say, he was making his offer plain and clear to me.  He'd let me use his power on myself.



A chance to communicate, to fix something.



I sensed my bugs moving, shifting position without even moving a limb or wing.  Before I even grasped what was happening, I was moving.  I cut out with my knife, feeling like I was swinging madly into open air.



A girl materialized, shouting or saying something.  She'd appeared just a little in front of me, her back initially to me as I continued cutting, the actions jerky and stiff, uncoordinated and continuing long past the moment there was any point.  I could feel her body appear in my mind's eye, and I asserted control over her.



At my command, her hand moved up to her mask, raising it enough that she could press her own knife's point to the roof of her mouth.  One good \emph{push}, suppressing reflexes, and she'd impale her brain.  It was a good place to keep her, keeping any of her allies at bay.



I was left panting, my knife-hand trembling.  Someone had moved to get a bead on me with their gun, but boys in white had intervened to block the shot with their bodies.  The girl\ldots she'd been materializing, been making herself known, and I'd caught on a second before anyone else had become aware.



The man had stopped in his tracks in front of me.  Still in my control.



Was it a trap?  Probably.  People didn't like being controlled.  He'd have measures in place.  Maybe his underlings, maybe a device he wore.



Was the offer still tempting?  Yes.



I had him extend his hands, offering them to me.



Sometimes there was a need for making a \emph{point}.  He wanted to \emph{manipulate} me?  He could \emph{bleed}.



I cut.



The blade of my knife found the flesh of his palms twice in quick succession.  The slashes were as wild and frenzied as before.  My \emph{aim} was good, but my control wasn't.  A cut found the back of his forearm, tore deep through cloth, skin and muscle.



My next cut was comparatively feeble, though it hardly mattered.  A barrier appeared, a crystalline wall, and the knife bounced off.



All around me, people reacted.  My swarm shifted position, and were summarily buried in prisms of that same transparent, floating crystal.



I had that one member of my swarm start singing again and she was shot an instant later, electricity arcing around her armor as she collapsed, unconscious.



I had my \emph{bugs}, but-



I stopped.  The reactions, the calls of alarm and the occasional shriek, they extended beyond the ring of people that surrounded me.



It wasn't right.  The chaos beyond this one group, it should have left people blind to what was going on \emph{here}.  They shouldn't have been able to turn their backs on the others.



I was- it was \emph{parsing} wrong.  Didn't connect.



In that riot, that mob, there was no blood.  The girl I'd cut wasn't bleeding, the people in the crowd weren't dying\ldots only the hands and arm, held out for the knife to slash, were weeping with blood, only the older injuries, from a short time ago.



People wrapped their arms around one another, but bones weren't broken, limbs weren't disjointed.  The shouting and screaming wasn't directed at anyone in particular, nor were the powers that were actively being thrown around.  There were tears, but those same people were \emph{smiling}.



I hadn't counted on having to deal with this many people.



Too many with powers I wasn't familiar with.  The ones closest to me?  The ones I'd just been controlling?  I had a grip on them.  But the mob beyond was something else.



I felt a moment of trepidation.



My senses\ldots I was more disabled than I'd thought.  I couldn't make sense of what was going on beyond my swarm, could barely make sense of what was happening \emph{here}.



I moved, relying on two individuals to support me where my one leg wasn't working properly.  Not that the other was in great shape.  Two individuals, the clairvoyant walking behind, hand strapped to my shoulder-



I saw the forcefield woman in the crowd.  Taller than most, a curved, crystalline horn on her forehead.



The people surrounding my swarm were working to get back as I approached, but the press of bodies only had a limited amount of give.



A forcefield materialized just in front of me as my power reached the very front of the crowd.  I turned the newest additions to my swarm around, focusing them on the people who were looking to stop me.



My bugs got in her eyes, blocking her sight, crawled into her ears.



I felt as she bisected them with forcefields.   I was already using the device on my back to move \emph{over} the forcefield, getting a boost from the two who'd been supporting me to heave the clairvoyant up with me.



He came down on top of me, and we landed hard, but we landed on the opposite side of the forcefield.  Close enough, taking advantage of the woman's momentary blindness.



I lowered forcefields and set them in circles around me before pushing \emph{out}.  Separating the crowd to give myself room to maneuver.



I needed to escape, I needed time and resources to analyze what I was up against, frame it all.  I'd stabilized, I'd stopped degrading, now I could start building- \emph{rebuilding }my knowledge base.  Put everything into a context that I could grasp, with my mind working in a different way, with different priorities.



\emph{Then} I could take control.  \emph{Then} I could eliminate the problematic elements.



\emph{Then} everything would be peaceful.



A mission.  I functioned best with a mission.  My thoughts and actions had always processed best when I had a mission, a \emph{task}.



I moved my swarm.  Half of the original sixteen, they'd serve as bodyguards, protection, \emph{tools}\ldots



I saw faces in the crowd.  Young women riding a monster, blocking my path.  More than any of the others, they were \emph{strangers} in the manner I'd identified the rest of the crowd before.  People I had some connection to, all the more \emph{strange} because of the lack of recognition.



People kept getting in my \emph{fucking} way.



I could have gone through, but I felt a moment's trepidation.  The strangeness, the strength of the connection.  They were enemies, friends, \emph{something}, but they held an importance.



I couldn't trivialize that.  Couldn't dismiss them.  If they were that important, they couldn't be \emph{weak, }and that meant they were potential threats.



She had a hand extended.  Something dangled from one hand.  A short chain, a black tube with a red button.



That trepidation got worse.  I couldn't put my finger on \emph{why}.



The uneasiness reached a peak.  I gave them one final look, watching for any trouble, then took to the air, crouching on a forcefield.  The members of my swarm followed, flying around any barriers I erected.  A man in blue and white who zig-zagged around anything I put up.  A regal woman in blue.



Too many unknowns.



I changed my course, and I saw the woman with countless wings standing, the wings spreading, a weapon at her side.



My pursuers were backing off, keeping a certain distance or circling around, giving her a wide berth.  Was this a way through?  If I leveraged enough strength, could I force my way past her?



I was scared, but it wasn't the usual kind of fear.  Almost the opposite.  I was used to being able to hold things together, with only the outward signs.  To channel fear into concrete \emph{purpose}.  This was different, the outward signs limited at best, the underlying fear simultaneously affecting me \emph{more}.  Like so many things, it felt alien, like I wasn't certain of what I was doing, and it threatened to throw me off course.



That fear reached a crescendo as I closed the distance.



She aimed the little gun, and I changed course at the last second.



There was a small army after me now.  Some were in the lead, and I made a point of blocking them, stalling with forcefields and directing ranged fire their way.  The man in blue and white was chief among them, as was the blue woman in a regal costume.



More were moving to follow.  Enemies from every corner.



Not a surprise.  To be expected.



A man, flying with great skeletal bat wings, a kind of lace or filigree of bone stretched between segments, rose into the air to intercept me.



No, to intercept a member of my \emph{swarm}.



My swarm worked to cut him off, but he was agile, persistent.  As massive and bulky as those wings seemed, they shapeshifted in the process of each flap, the lattice of bone opening up to let air pass through, then closing when he wanted the air resistance to bear himself higher, or to one side.



In the end, a forcefield appeared through one wing, and he dropped a solid thirty feet before he managed to catch himself.  It gave me a window of opportunity.



The path of least resistance\ldots  There was another space with only one person in the way.  A gap in the defensive line.



It was a young girl that was barring my path.  Her blond hair stirred in the wind of this upper atmosphere, and her great green-black costume seemed more decorative than anything else, with ribbons and loops of cloth flowing in a manner that made her look like a living work of art.



She wasn't living art, though.  As remote as my understanding of humans was, I could understand what her tears meant.  There was no smile accompanying them.



Others had stopped, a distance away.  Not wanting to interfere, even afraid.



She met my eyes, and there was something in her expression that I couldn't quite place.



The man in white and blue was calling out, not orders, but something in that vein.  Urging.



I looked at the blond girl, and I saw three shadows form around her.



My own swarm gathered, rising behind me on the floating shards of crystal.  Some crouching, some standing, others sitting with legs dangling, as they preferred, running on autopilot.



She approached me, and I held her gaze.



She passed into my range, and -again- I felt the connection deviate.  I maintained my awareness of her and her spirits, but my control over her slipped to one of her shadows instead.  A shadow of a robed man with a blindfold and nails through his hands, wrists and upper arms.



The other two – I recognized their powers.  A man with access to many powers at once, a fluctuating, flexible thing, and an thin, plain looking man with no costume, head hanging, with the power to make doorways.



She closed the distance, and her hand touched my cheek.  I flinched away.



I had my knife.  If I couldn't control her-



She bowed, stepping away.



I felt a moment's fear.  Except `fear' was the wrong word.  The symptoms were right, if muted, the shakiness, the feeling in my gut, my thoughts being more fractured, a touch of queasiness.  But it didn't fit the scene, this meeting.



Why would I be afraid?



No, it was something else, and I was realizing what it was.



I was familiar with my power acting of its own volition.  This was something in that vein.  My power had a firmer grip on the whole of \emph{me}, and other things were on shakier ground, acting the way they pleased.  Feelings.  My body.



Passenger.



No, why would it care about any of this?  Why would it care about the winged woman?  The two individuals who'd been riding the monster?



But it was the closest feeling I could manage.



She spoke, and I couldn't understand the words.



When she saw that, she smiled a little, glancing over my swarm.



A doorway opened beside her.  She floated away a touch, as if inviting me through.



I hesitated, at first, because of suspicion.  I had \emph{worlds} filled with enemies, worlds I needed to bring under my thumb if I was going to be able to relax for even a moment.



I forced the worries aside.



I felt another stab of that not-fear sensation.  That \emph{balking} on the part of my passenger.



The others around us were moving closer.  There were angry shouts from some corners.  There was a degree of attachment between some of them and my swarm.  I raised forcefields.  The man in white and blue promptly shattered them with a massive laser.



We were left staring at one another.  I couldn't move forward, couldn't move back.



Contradictions, opposing forces.  Some threatening me to stay, others threatening me \emph{if I stayed.}  Contradictions in equal measure inside me.  That odd dissonance.



I stared at the portal.  A point of no return.  I could pass through, and I'd be able to take steps to get control, to carry out my plan.



-Again, that dissonance.



It was uncomfortable, distracting.  I wanted to be able to pursue my goals unmolested.



I started to move towards the portal, and again I felt the trepidation, halting me, threatening to take my control altogether.



I closed my eyes, and despite every instinct telling me to do the opposite, I relaxed.



Forgetting about the mission, about the goal.



I could feel the shakiness returning, the unsteadiness.



\emph{W-wwha- ddo y-y-you wwwant}?



My control was slipping, the others descending as the forcefields lost altitude.  The forcefield woman nearly slipped out of my range altogether.



I reasserted control.



Again, I tried to let my passenger take control, to set things on autopilot.



\emph{Again}, the others began to descend.  This time, the forcefield woman remained where she was.



I let things continue, watched as they drifted away, back to the ground.  The others gathered around me, the man with the blue and white costume, the man with bone wings, they backed off a little.  I could see the latent aggression dissipating.



Some were still angry, still looking for revenge.  The woman in blue seemed more angry than protective, furious at \emph{me}, silent as she was.  But she had less backup now.



It was a good move, for the short term.  A puzzling one, but a good move.



I'd have a harder time taking control of things in the long term, but I was okay with survival.



I watched the individual members of the swarm touch ground.  The girl with healing powers had been placed deliberately next to a living pool of flesh with multiple heads of golden hair.  The healer's hands were covering her face, but she didn't step away.



Her hands slowly lowered, and she laid her eyes on the monster, which was actively, ineffectually reaching out for her.



Others were placed indiscriminately in the crowd below me.  My swarm, returned to the place they came from.



I turned to go, and there was far less resistance.



The autopilot took control of the clairvoyant's focus.  It turned my attention to faces.  A blond girl.  A girl with brown-red hair.  The girl with the horned mask that I'd attacked so ineffectually with the knife.



Others.  A red haired girl in another world, shouting to people as she ordered them through a building project, a girl who was standing outside in the rain, in another world, kids peering through the window behind her.



Before it could go any further, I wrested control for myself.  Easier.  It was like it was weaker with every set of actions.



I passed through the threshold.



Again, that discomfort.



This would be a learning process, adjusting, adapting.  I was learning what it wanted.



It kept wanting sacrifices in the short term.  Responding to its desires had left me feeling more secure, made the ensuing resistance weaker.  The implicit promise was that acquiescing would be rewarded with a surer footing.  Footing that I could \emph{use.}  There were doors open to every world.  If I could take time to heal, to build my strength.  Eating well, resting\ldots I could move on, carry out my plan.



The question was whether the cost was too high.



It was a gamble.  I was risking myself, setting myself back.  People would come after me.



But it meant more control, and it all came down to control in the end.



I let the clairvoyant step through the portal, onto the shard I'd just abandoned.  The forcefield woman held on to him, steadying him.



I broke contact.



The last thing I saw before I passed out was the door closing.



\blacksquare



I opened my eyes.  The moon was too bright, the stars like little shards of glass piercing my eyes.  When I sat up, I felt muscles in my neck, back and shoulders seizing up, cramping.  The world swayed around me like I was on a boat, even though I was on a hill in the middle of a forest.



I was hungry.  It had been a day, maybe two.



I heard the cocking of a gun.



My eyes shut.



Long seconds passed.  I took the time to get my bearings, to catch my breath and let the world stop rocking around me.



When minutes had passed and things were bearable, I turned to give my attacker a sidelong glance.



Twenty feet away, sitting on a rock with a little messenger bag beside her, was a woman in a white dress shirt and suit pants.  Her gun was in hand, a little revolver, resting on her knee, her suit jacket draped over that same knee.



Strangely, I felt none of that odd fear from my passenger.  Just the opposite, if anything.



The woman spoke.  The words didn't make sense, but I \emph{understood} them\emph{.  }



Where the words themselves were nonsensical, my brain tried to parse them anyways, and they found a degree of sense in my head.



``\emph{You knew it would come to this.}``



I didn't move, staring.



Speech.  It affected me more than I wanted to admit, hearing it.  Even if I grasped the meaning.  Brought me back to myself, just a little.



``\emph{You don't remember me, but if you don't look too hard, you'll be able to tap into vague recollections of who and what I am.  You should know I have you in checkmate.  There are no loopholes, no tricks, no ways out.''}



My eyes moved over the area.  I did what she suggested, and I could pick up a general impression of our past encounters.  We'd crossed paths before, and I'd lost absolutely.



If we fought here, I'd lose again.  Especially like this.  I'd try something, she'd shoot.  The bullet would kill me faster than my swarm would kill her.



A feeling of \emph{defeat} settled on my shoulders.



``\emph{Water?}\emph{If you speak, I'll understand.}``



``Yes,'' I said.



She reached into the bag and grabbed a thermos.  She threw it, and the corner of it sank into the dirt between my knees.



I drank greedily.



``\emph{What you are, you know you can't be allowed to carry on.  You don't quite remember, but you've dealt with some who were like you.  The Echidna, the Faerie Queen.  You saw the Ash Beast.''}



``Hearing the two\ldots first two names makes me feel\ldots shadows of feelings.''  Talking was hard.



``\emph{I imagine so,}'' she said.  ``\emph{We walked very similar roads.  We've done ugly things for a greater good.}``



``You still-'' I started.  Then I shut my mouth.  Why had I talked?  I hadn't meant to.



She raised one eyebrow.  I didn't understand what the expression was meant to convey.



``\emph{Go on},'' she said.



``I don't-'' I started.  What had I been saying?



Not me.  The passenger.  I had to relax.  Allow myself to speak.



``You still do ug-ly things.  I saw you with T-teacher.  You work with him now.  As before, still do now.''



``\emph{I'm not so sure,}'' she said.  ``\emph{There's less of a mission, now.  I have no cause anymore, and I hope that means I don't lose sight of the little things.}``



I didn't have a response to that.



Instead, she volunteered a little more.  ``\emph{I'm thinking I'll try to do some things without any help, in the future}.''



I stared down at my knees.  I was still sore from my unconscious posture on the hard ground.  She was talking about the future, and I didn't have one.



``\emph{I keep on asking myself the same questions over and over again},'' she said.  ``\emph{Maybe you can answer.  Was it worth it?}``



I stared down at my hand.  It was shaking, but it wasn't from fear.



``\emph{Would you do it all over again?  Knowing what you know now?  Knowing that you end up here, at gunpoint?}``



``I\ldots know I'm supposed to say yes,'' the words made their way past my lips.  ``But no.  Some-somewhere along way, it became no.''



``\emph{Just about everyone comes to this crossroad,}'' she said.  ``\emph{Some get seventy years, some only get fifteen.  Enough time to grow, to take stock of who you are.  Enough time to do things you'll regret when you run out of time.}''



``Don't- don't regret it.  Was- had to.  Saved lives.  But I would do different, given a chance.''



She smiled, bobbing her head up and down a little.  ``\emph{It's always about the people, isn't it?}''



``Protect some, pay less attention to others.''



Her smile twisted.  A little sad.  ``\emph{Can't bet on the wrong horse.}''



Not what I'd meant.  ``Giving too much power to wrong people.  To bullies.  With powers, bullies without.''



She gave me a slightly surprised look at that.  ``\emph{I don't see that applying to Scion.}''



``Doesn't.''



``\emph{He doesn't factor?  He isn't a consideration, at the end}?''



``Fighting him\ldots always more about \emph{us} than about him.  Not a consideration.''



``\emph{And the person who played the biggest role in stopping him doesn't give him a second thought,}'' she said.  There was a note of emotion in her voice.  She was gripping the gun handle tightly enough that her knuckles turned white, but her expression wasn't an angry one.



I didn't respond.  I felt like it might have been rude to.  We all had our demons, our burdens, and this was hers.



The silence yawned on.  I took another gulp of water from the thermos, swallowing past a lump in my throat.



I looked at the trees.  I was reminded of\ldots the scene was hard to reach.  Of home, not long after it stopped being home.



Was it the other way around?  When I imagined that rotting, flooded city that smelled like garbage and seaweed, what was it to me?



Or was it different things to the two biggest pieces of me?



``\emph{They're offering amnesty to all but a few},'' she said.



I wasn't surprised.



``\emph{The Faerie Queen was brought in.  You should remember her.  She's the one who let you go.}''



``Yes,' I said.



``\emph{There were a lot of eyes on you two, at the end.  It reflected well on her, that she got you to free the captives.}''



She hadn't, but I didn't explain.  This woman probably knew, anyways.



``\emph{She was questioned about you, in the hopes that the heroes could use the information to find you.  I got the transcription of the interview,}'' the woman in the suit said.  She patted the bag.  ``\emph{I could use my power to get the answer, but it's been a long journey here, and we're in no rush.  Do you\ldots does the word `anchor' mean anything to you?}''



It took me a second, but I nodded a little.



``\emph{What did you pick, in the end?}''



I opened my mouth to answer, but I found only blanks when I reached out.  I closed my mouth.



``\emph{Ah},'' she said, as if that was answer enough.



``A-ah?''



``\emph{She went to great lengths to protect you,}'' the woman said.  ``\emph{She's already on shaky ground, but\ldots I think she saw herself in you.  She held out hope that you'd found yourself.  That she'd have a kindred spirit in you.  It might even by why she balked at the end.  Seeing you, realizing she'd built herself off of a lie, compromising too much with her agent.  In that decisive moment, she did something honest.  Maybe you inspired that.}''



Was I honest?



``\emph{Were you honest enough to inspire that?}'' the woman asked, echoing my thoughts.  ``\emph{It's\ldots probably the most important question I'm going to ask you tonight.}''



I'd started my career on a lie, an undercover operation.  I'd ended it by betraying what I stood for.



``\emph{I think you have the capacity to answer,}'' she said.  ``\emph{You're more lucid than you were.}''



``Talking\ldots talking helps.''



``\emph{That's part of why I'm asking, Taylor Hebert.  Weaver, Skitter, Khepri, I'm thinking you're not totally gone.  Glaistig Uaine told you to hold on to an anchor.  The other ones, the little ones?  They might have gotten you through the events, given you the strength from moment to moment.  But you had something bigger.  Something more fundamental, which was there before the battle even began.}''



I knew she was right, but-



``\emph{Were you really a monster in the end?  A warlord, an alien administrator?  A vicious killer with a cruel streak, mutilating your enemies and secretly enjoying it?  A bully, if you forgive me for using that word?}''



I looked down at my hand.



``\emph{Or were you really a hero?  Do the good intentions win out? }\emph{Was it Glaistig Uaine's strength or yours, that held her back from saving Scion in those final moments?}''



``Why\ldots does it matter?''



``\emph{Because I think you have a chance to come back from this.  Not much of a chance.  Part of that rides on me.  I could help you, or I could stop you from troubling anyone ever again.  Part of that?  It's up to you to win the fight, to take control and keep the administrator from claiming everything you have, leaving you a shell.}''



I felt a chill.  Was part of it my passenger?  Both of us?



I opened my mouth to reply, and I couldn't.



Didn't deserve to, either way.



``\emph{It's okay.  I got the answer, myself.}''



I looked away.



I looked \emph{up}.  My eyes were wet.



So many stars.  The universe so vast.



\emph{We're s- so very small, in the end.  }



The first bullet hit me from behind, where my mask offered no coverage, and I slowly toppled.  The second hit me before I could fall, before there could be any pain.





