





I squared off against a very thin Japanese man of Grue's height.  He held a knife in one hand and a katana in the other.



A narrow smile crossed his face as he made his katana blade whip around himself at lightning speed.



At my command, a swarm of wasps flowed from beneath the armor of my costume and set themselves on him.  There was a moment of bewildered swatting before he started howling in pain.  Both katana and knife fell to the ground as he started using his hands to flail at the swarm.



I drew my baton and struck him across the bridge of his nose.  I wound up hitting him much harder than I intended to, as he just happened to bend forward at the same moment I swung.  As he reeled, blood streaming from his face, I lunged forward with a low swing to hit him in the side of the knee.



He crumpled to the ground and writhed, in too much pain to retaliate.  I bent down to pick up the knife, which looked cheap, and the katana, which looked antique.  I used the knife to cut the katana's sheath from his side, then dropped the knife and kicked it into a storm drain.



With the sheathed katana in one hand and my baton in the other, I looked over the evening's battlefield.



The building that loomed over us was a tenement, like countless others in the Docks.  Five or more apartments in an area so small it should only hold three at most.  Ten or twelve families sharing a single bathroom and shower.  That reality was ugly on its own, but word had been that the ABB was turning tenement buildings like this one into barracks for their soldiers.  That the less than enthusiastic recruits, the ones with bombs implanted in their heads, were being gathered up here so they could be watched, trained, equipped, and deployed by the ABB's captains.



I'd balked at first.  I'd been worried that it was a ploy on Kaiser's part to get the organized villains of Brockton Bay to attack a building full of helpless people.  Even after Tattletale had confirmed this was an ABB base of operations, I'd had my doubts.



Had my doubts, that was, until we'd attacked and ABB soldiers had flooded out of the building like ants from an anthill.  Clowns from a clown car.  A ridiculous number of people, anyways, for a building that wasn't all that big.



We were outnumbered twenty to one, but I doubted any of us were really breaking a sweat.  There was nobody with powers fighting in the ABB's defense, since only Bakuda was uninjured and we had an idea of where she was holed up.  That meant that all we had to worry about were their rank and file gang members, and we'd already taken out the guys with guns.



Blazing fires as tall as I was dotted the road around the tenement.  In other spots, patches of darkness lingered.  There was no power to the area and there hadn't been any for days, probably the military's work, and the battlefield was lit by the flame alone, giving the ongoing fight had an almost hellish appearance to it.  The faces of the ABB members contorted in pain and fear.  The villains advancing, implacable, with faces like Grue's skeletal helmet, Spitfire's modified gas mask with the lenses reflecting the flames and Gregor's doughy face with barnacle-like bits of shell crusting it.



And me, I supposed.  The yellow lenses of my freshly repaired mask, mandible design framing my jaw.



I headed towards where the fight was mainly happening, and came face to face with a twenty-something man.  I immediately pegged him as one of the recruited.  Someone who wouldn't be fighting if it weren't for the bomb planted in his brain.  He held a baseball bat pointed at me like it was a blade.



``Surrender,'' I told him, ``Put the weapon down, lie on the ground and put your hands on your head.''



``N-no.  I can't!''



``I've got powers.  You don't.  In the past ten minutes, I've taken down people bigger than you, with better weapons, people with killer instinct, and I did it without a sweat.  I'll tell you right now, you lost.  You'll lose this fight.  Lie down and put your hands on your head.''



``No!''  He stepped forward, raising the bat.



I didn't like fighting these guys.  Didn't like hurting them.  But if they wouldn't surrender, the next closest thing I could offer to mercy was hurting them obviously enough that their willingness to join the fight wouldn't come into question if he wound up having to explain to Bakuda.



I set my bugs on him, hoping to distract him enough to buy me time to deliver a decisive blow.  This guy, though, he didn't buckle.  Rather than struggle, he charged headlong through the swarm of biting and stinging insects, blindly flailing his bat in my direction.  I had to scramble backward to avoid being clubbed.  I drew my baton back, tried to decide when and how to strike.  If his bat hit my baton, he could disarm me.  If I could hit his hand, though, or catch him with his guard down\ldots



There was no need.  Grue stepped in, almost casually, and put his fist through the poor guy's jaw.   He crashed to the ground, the bat sliding out of his hands.



``Thanks,'' I said, even as I winced in empathy for the guy that had just been knocked out.



``No prob,'' the haunting vibes of his voice were at odds with his casual choice of words.  ``We're nearly done here.''



I glanced around the battlefield.  Injured and unconscious ABB members littered the ground around the building.  Though we'd been outnumbered at the outset, only a few stragglers remained.



``Tattletale!'' Grue bellowed, ``How many?''



``This is it!  Building's clear!'' she called back.  Following her voice, I saw her crouching on top of one of the few cars parked along the street, gun dangling from her fingers, out of the way of the fight and with deterrence in hand.



``Spitfire!'' Grue called out.  ``Snail!''



The two members of Faultline's team worked in tandem.  Spitfire set about spewing a geyser of fluid out of the nozzle at the base of her mask, directing it to the base of the building, where it ignited on contact.  Gregor the Snail, in turn, reached out with one hand and blasted out a steady stream of foam at the adjacent buildings.  He'd informed us before the fight started – he could concoct a variety of chemicals in his prodigious stomach and project them in a stream from his skin.  Adhesives, lubricants and strong acids, among other things.  The one he would be using now would be something fire retardant, as we'd planned.  It wouldn't do to burn down the neighborhood.



While Spitfire worked on burning the building to the ground, and Gregor kept the blaze contained to the one building, the rest of us spent several minutes working on disarming and moving the injured and unconscious enemies from the building's vicinity.  Grue had supplied me with a package of dozens of plastic wrist-cuffs, and I started making use of them on the ABB members.



Grue approached me, ``I ran out.  Got extras?''



I handed him a fistful of the wrist ties.



``So this thing with the ABB is almost over,'' he said, ``And I was talking to Fog, one of Kaiser's people.  Sounds like he's not going to press the issue over Bitch and the dogfighting thing, like you suspected.''



I nodded, ``Good.  I don't like them, but that's a fight we don't need just yet.''



Grue wrestled with a gang member with an injured leg, twisting the guy's arms behind his back and then punching him in the kidney when his struggling made it too difficult to get the plastic handcuffs on.  The guy gave up the fight.



``You got any plans for tomorrow?''



I turned my attention away from the unconscious girl I was cuffing and looked at Grue.



``Well?'' he asked.



``I'm planless.  No plan,'' I fumbled my words.  Technically, I could or should be going back to school, but I still had the tentative excuse of the concussion, so I could get away with missing another few days.  After the way the meeting with the school had gone, I was glad for the excuse.



``Want to come over to my place?  I'm supposed to have a group meeting to discuss progress and whatever for this online class I'm taking, but I've also got my sister's caseworker stopping by to check out my apartment in the afternoon.  I was hoping to buy some furniture and get it put together by then, but I'm tight on time and it'll be a hell of a lot easier with two people,'' he told me, ``\ldotsand that was a rambling explanation.''



``I got the gist.  Yeah, I could do that.''



I had seen him smile that boyish grin of his often enough that I could picture it behind his mask.



``I'll text you with the time and address?''



``Alright.''



He gave me a very `guy' clap on the shoulder, then headed over to catch up to a guy that was trying to crawl away, a little ways down the street.



As he left, Tattletale joined me, taking a few wrist-ties from me, and helping me with others.  She was grinning.



``What?''



``Nothing.''



``You're reading too much into it,'' I told her.



``He didn't invite \emph{me},'' she gave me a sly look.



``Maybe he knows you wouldn't have accepted.''



``Maybe he suspects I would've, and he wanted to spend time with just you.''



I had my doubts.  Definite doubts, about what she was implying.  I didn't get a chance to clarify.



``Coming down!'' Gregor roared.  There was a rumble as the building began to sag, followed by a crash as it started folding in on itself.  Spitfire directed her napalm breath to one corner of the building, obliterating the wood and stone there.  She swiftly backed up as the building finished its controlled collapse.



As the rubble settled, Gregor sprayed his extinguishing foam with one hand, directing the stream against the fingers of his other hand so the stream separated into a broad spray.  Where each of the droplets hit a part of the building, they swelled into a blob of foam a few feet across.  In short order, the building was covered enough that only a few traces of flame were still visible.



``We're done, let's move!'' Grue called out, returning to where Tattletale and I were.



We scrammed, leaving the thugs tied up, while Spitfire and Gregor the Snail disappeared down a different street.



We'd broken into a dilapidated old mechanic's shop to stash our ride, and we returned there in short order as Tattletale made a call to the authorities about dealing with the ABB members.  As the car pulled out and headed towards the water, I let myself breathe again.



Our third night like this since Bitch and I had gone up against Lung.  Each night had been easier than the last, and I wasn't sure how much of that was me getting more comfortable with things, and how much was the fact that the ABB was falling apart under the sustained onslaught.



``I think the ABB is just about done,'' Grue spoke from the driver's seat, echoing my thoughts and his earlier statement.



``Three days and nights of pressure from the police, military, all the good guys and most of the villains in the city will do that,'' I said.



Lisa commented, ``It's like I was telling you, Taylor, someone breaks those unspoken rules, the community protects the status quo.  Us villains make truce with the local authorities, we actually work together, in a way, with the cops, capes and military holding the line during the day, and taking down any ABB members who stick their heads up, while us villains do the nitty gritty stuff\ldots In this case, it's probably more blatant an invoking of that than any example I can think of.  Guess we can thank Coil for that.''



``It's been a learning experience,'' I added, ``If nothing else, I've gotten a better sense of the other groups.  I didn't think Coil's soldiers would be quite as good as the ones I saw in action.  Meeting the members of Faultline's crew, and the Travelers, too.  They're not bad people.''



``I learned a lot too, in a different way,'' Tattletale leaned forward from the backseat, putting her head and shoulders between the two front seats.  ``I said part of the reason I wanted to go with Trickster and his shapeshifter teammate was to figure out their powers, right?  I  never shared.''



``And?'' Grue asked.  One hand still on the wheel, he peeled off his helmet with the other.  It took only a second for the darkness around his face to clear up.



``And Trickster, their leader, is a teleporter.  Not just himself.  He can make anything he can see teleport.  Except there's a special rule to his power, a restriction.  He has to swap the places of two things with roughly equivalent mass.  The bigger the difference in mass, the slower the swap and shorter his range.''



``That sounds like a pretty large drawback,'' Brian said.



``He makes it work.  He had ABB members hitting their own guys, he was disarming them like it was a piece of cake.  As for the `shapeshifter'.''  Tattletale made finger quotes.  ``Her name is Genesis.  Her power?  Remotely controlled projections.''



``She's not actually there?''



Tattletale shook her head.  ``Showed up with a triceratops-bull-cyborg thing, charged through the front door, set off a trap, got blown to smithereens.  And Trickster just laughed.  Two minutes later, she'd pulled together a lady knight in shining armor and was dealing with the guys with guns.''



``Geez,'' I said, ``Sundancer's got a miniature sun.  Ballistic, as Brian and I saw just last night, just needs to touch something to have it go rocketing off at a few hundred feet a \emph{second}.  Doesn't matter if it's ball bearings or a car.  Add this new info, and well\ldots''



``Heavy hitters,'' Brian finished for me.



``We can be glad they're on our side,'' I said.



``For now,'' Brian pointed out, ``We still don't know why they're here and why they're helping.''



He glanced at Tattletale, eyebrow raised.  She shrugged, ``My power's not telling me anything concrete.  I'm as curious as you are.''



I joined Brian in pulling off my mask.  The car, supplied by our boss, had tinted windows, so there was no stress there.  I'd have to put it on again when we made our way past the military blockade, but that wasn't such a problem.



I lowered the sun visor above the windshield and used the mirror to examine my neck.  The bruise was still noticeable, there.  Much as Bitch had said, it looked like I'd survived a hanging.



``Mind if I stay over again, tonight?'' I asked.



I saw Tattletale shrug in the backseat, through the mirror.  ``It's your place too.  You don't even need to ask.  I think you should call your dad, though, so he doesn't worry.''



``Yeah, call your dad,'' Brian confirmed.



``Alright.''  I was going to do that anyways.



When the military barricades with flashing lights atop them came into view in the distance, we pulled into the loading area for what had once been a small grocery store, out of sight.



``Any rush?'' I asked.



``We're good,'' Tattletale said, ``I'm going to call Regent and Bitch, see how their group is doing.''



``Then I'll call my dad.''



I stepped out of the car to make my call.



He picked up on the first ring.



``Hi dad.''



``Taylor.  I'm relieved to hear from you.''



So he'd been concerned.



``I'm going to stay at Lisa's again, tonight.''



``I'd like you to come home, Taylor.  It worries me that I haven't seen you since you left the meeting at the school.''



``I'm okay.''



``It's not that I don't believe you, but I'll feel a lot better when I see that for myself.  I want to talk, have dinner and breakfast together, touch base.  I don't want to lose touch like we did after\ldots''



``After mom died,'' I finished for him.  ``It's okay, Dad.  I just\ldots I guess I needed a change of pace, to get away from it all for a little bit.  I already made plans for tonight.  It'd be awkward to cancel.  I'll come home for dinner tomorrow?''



He hesitated.  ``Okay, just tell me you're going to school.''



``Yeah,'' the lie passed through my lips easily, but it sat heavy on my conscience.  Disappointing him would have felt worse, though.  I tried to take the edge off the guilt by making it a half-untruth, ``I didn't go Monday.  I started going yesterday afternoon.''



``I suppose that's better than nothing.  I'll see you tomorrow night, then.''



``Love you, dad.''



``Love you too.''



I hung up.  It was a white lie, right?  I wasn't really hurting anyone, and my dad would only worry more if I told him I wasn't going to school.



Tattletale and Grue climbed out of the car as I pulled on my mask.



``All set?'' she asked.



``Ready,'' I answered.



She opened the hatch at the base of the grocery store, that would lead us into the tunnels that stretched beneath the barricade.



We descended into the darkness.





