





There was something exhilarating about living without adult supervision.  It wasn't that I didn't love my dad to death, but waking up, going for a run, making breakfast and then sitting down in front of the TV with one of Lisa's old laptops, without feeling like anyone was looking over my shoulder to make sure I was doing everything right?  It was the life.



Since the week I had spent bedridden with the concussion, I had been twitching to get back into my running schedule again.  Even though I was staying at the loft, taking a vacation from my everyday life, I was making a point of keeping to my old routine and waking up at six thirty in the morning to run.



As it happened, that meant I was waking up two or three hours before any of the others.  Two or three hours totally on my own.  If I forced myself to ignore the thousand different things I could be stressing over, it was a period where I could enjoy a peace I hadn't felt in a long, long time.



I'd curled up on the couch with a blanket around me, a kid's show on the TV for some low level background noise – since it was the only thing on besides infomercials, religious programming and talk shows – and I had one of Lisa's old laptops propped up in front of me.  My habit now was to start the day by checking the local news sites, the parahumans wiki and the parahumans message boards.



The big front page scoop of the morning was a picture someone had taken with his cell phone from one of the buildings on the same street as the building we'd burned down.  Our silhouettes were visible as we stood on the street with dozens of ABB members strewn around us.  The headline? `VILLAINS STEP IN'.



Funny, I never really noticed the bugs when they were around me in general, but seeing the picture, there was a good number.  My silhouette wasn't as hard to make out as Grue was in his darkness, but it wasn't easy to make out in the cloud of bugs, either.  I had to keep that in mind – maybe I could use it.



The article beneath the picture was about the actions of the villains in dealing with the ABB.  It was mostly on target, but the tone and slant of the writing made me uncomfortable enough that I didn't read it in depth.  From my skimming of the article, I got the impression the heroes were gearing up to make a final assault today or tonight.  Let us do the dirty work and then clean up?  Whatever.  If they wanted to deal with a cornered Bakuda, they were welcome to it.



I browsed the other news:  A tally of injuries and deaths that had occurred since the fighting started, estimates on property damage sustained from the various bombings, a brief update on a twelve year old girl that had gone missing two weeks before the ABB situation started, that was now presumed dead, and descriptions of some of the new heroes to show up in Brockton Bay to help with the ABB.  What caught my eye was a censored image in the gallery sidebar of the last news article.  I clicked it.



It was an image of Lung in his human shape, his eye sockets dark, raw and empty behind his steel dragon mask, his hand on one of his gang members' shoulder.  It seemed like he was being led.



It was, I discovered, the image that ended the `Villains Step In' article featured on the front page of the site.  I'd missed it when glancing over the article, because the flash image viewer had taken so long to load.  There was a caption beneath it.  `Decisive blow?  Brockton Bay authorities have turned a blind eye to local villains enforcing their own brand of justice.'



Oh man.  Was I digging myself in deeper and deeper?



That same image gallery had a long range shot of the same scene, taken without the telephoto lens, showing Lung and his flunky in the midst of the Docks and an armed squad of their men, guns drawn but not raised at anything.  That was\ldots massively disappointing.  He'd gotten away.



``Morning,'' Lisa greeted me.



I turned to see her coming from the kitchen.  Her hair was tied back in a messy ponytail, and there was still sleep in the corners of her eyes.



``Morning.  Brian said he had something to do this morning, so I grabbed you guys your breakfast today.  Sorry if I didn't get the coffee exactly right.''



``You're an angel,'' she messed up my hair, then left to get the coffee.



I was still browsing when she returned.  She bent down, folding her arms over the back of the couch behind me and watched over my shoulder for a bit.



``Pink haired singing pirates and blind yakuza wannabe supervillains.''



I glanced at the TV, and sure enough, there was a little girl in a pink wig with a pirate costume.  I smiled and held up the remote, ``You can change the channel.''



As she took the remote, my cell phone buzzed on the couch cushion beside me.



Brian had sent me a text:



finished early.  two didn't show.  want to come @ 11am?  or I can pick you up @ loft



I glanced at the clock.  9:45.  I used the laptop to figure out the fastest bus route to his place.  It was downtown, and I could get there for eleven if I left in twenty minutes.  A bit tight, timewise, but I could pull it off.  I'd done it a few times before school, when I'd overexerted myself on a morning run and had to walk home.



I sent my reply:



Sounds good.  I'll take the bus.



Once I'd verified the message was sent, I bolted for the washroom and cranked the shower on.  I spent an age getting the temperature tolerable, stripped out of my running clothes and jumped in, only to have the shower change abruptly from a lukewarm temperature to icewater.



Loved the loft, did not love the water heater.



I had to dance around the stream of hypothermia-inducing spray to get to the controls and attempt to coax a decent temperature out of them.  I finally settled for a bearably cold temperature, shampooed and stuck my head under.  I was shivering when I turned the water off.



I dried off best I could and bundled myself up in a second clean towel for warmth.  Having no body fat sucked sometimes.  I finished my grooming and stopped by the living room for a second to peek at the clock below the TV.  I had six minutes left to get ready.



``It's so very \emph{you}, how you use perfect punctuation and capitalization for your texts,'' Lisa grinned as I headed for my room.



She was walking out of the kitchen, holding my cell phone.  I grabbed the phone from her, rolling my eyes, and headed to my room.  She followed me and let herself in.



``You two going to be an item?'' she asked.



``Not the plan.  Just going over to help out a friend.''



``Come on, we both know you think he's good looking.  Admit it,'' she turned her back to me, examining the amber with the dragonfly in it, that Brian had given me.  I used that brief window of privacy to dig some underwear and socks out of a drawer and start getting dressed.



``This is you using your power?''  I asked her.



``\emph{Brutus} is probably aware you're attracted to Brian.  I think the only two people who haven't figured it out are you and Brian.''



I sighed.  ``Yeah, I think he's a very good looking guy,'' I pulled some of the shirts and skirts I'd bought with Lisa out of my closet and arranged them on the bed, ``Don't you?''



``Sure.  Maybe not totally my type, but I definitely wouldn't turn someone like him away, if I was doing the relationship thing.''



``You're not?  How come?''



``My power kind of takes the mystery out of things.  Relationships are hard to get off the ground unless you can get the ball rolling with a healthy dose of self delusion and lies.''



``So you're not going to date ever?''



``Give me a few years, maybe I'll lower my standards enough to be able to overlook what my power's telling me about the guys' more disgusting and degrading character quirks and habits.''



``Sorry to hear.''  I replied, as I put some clothes back in the closet.  I felt bad for not being able to come up with a better response and for not being able to take the time to sympathize, but I barely had any time left to get ready.  Maybe I could jog to the bus stop.



``But the key distinction between you and I, here, is that Brian and I would kill each other before a relationship got anywhere.  You two, though?  I can see you working.''



``That your power talking?  You're saying he actually likes me?''



``Sorry, hon.  Reading people with my power is hard, reading into their motivations or emotions is harder, and to top it off, I don't think even Brian knows what he's feeling, romantically.  You might have to jar him from his comfort zone before either of you get to find out.''



``You're assuming I want to.''  I felt a bead of cold water run down the back of my neck, shivered and stopped to wring my hair again.



``Don't you?''  She asked.  She turned her attention to my selection of clothes piled on the bed.  ``You're paying a lot of attention to what you're going to be wearing.''



``I always do, even when I'm just going to be hanging out with you and Bitch.  I second guess and stress over the clothes I'm wearing if I'm walking to the corner store by my house to buy milk and bread.''



``Fair.  Here\ldots Let me pick the clothes, and if anything goes wrong, you blame me, deal?'' She dug through the clothes in my closet, ``Jeans and\ldots let's see\ldots a crop top to show off that belly of yours.''



I looked at the top, it had a thick fabric that bordered on sweaterlike, blue and gray with a sketchy sort of design of a butterfly on it, and long sleeves.  The actual body of the shirt, though, didn't look like it would reach much past my ribcage.  ``It's still a little cold out.''



``Wear a sweatshirt or a jacket, then.  But only if you promise to take it off when you get there.''



``Fine.''  I didn't have time to argue, and started getting dressed.



She started putting away the stuff I'd left on the bed, ``Brian's a guy who appreciates being practical.  That's something he likes about you, and he's said as much.  And even though I think it's fucking fantastic that you're going a step further to look nice, you can do that in clothes that make sense for doing light labor.  Jeans, yes.  Skirt?  Not so much.''



``Guess I wasn't being practical just now.''  I pulled on the top and looked myself over in the mirror on the closet door.  Agreeing to this top had been a spur of the moment thing when I'd been shopping with Lisa.  Actually wearing it was something else entirely; the bottom of the top stopped an inch shy of my belly button.



``You've got stuff on your mind with school and your dad and romance and shit.''  She answered me.  Before I could argue there was no romance happening, she gave me a push, ``Now go!  Enjoy yourself!''



I took that as my cue to hurry to the front of the loft, where I slipped on my running shoes.  I grabbed my keys and wallet from my backpack, grabbed my sweatshirt from a hook by the stairs, then headed downstairs and out the door with everything still in my hands.  As I got outside, I put my keys and wallet in my pockets and pulled on the sweatshirt.  It took a little willpower, but I left the sweatshirt open.



A relationship with Brian was, obviously, a terrible idea.  I was only expecting to be with the Undersiders for another two weeks to a month.  Any longer than that, and I'd probably assume I wasn't going to get the dirt on their boss, at which point I'd take what I had to the Protectorate.  Assuming there was enough interest on Brian's part for there to be a relationship in the first place, the idea of dating with no future was just depressing.  It would just wind up being salt in the wound for everyone involved.



But I was trying not to think about that.  I really didn't need Lisa reading into my doubts and hesitations and realizing that they were at least partially based on the fact that I was planning on betraying her and the others.  If I didn't dwell on it, it would be that much harder for me to give her any clues.



Yep.  Totally the reason I was avoiding thinking about it.  Nothing to do with the fact that I was feeling increasingly lousy and ambivalent over the idea of turning friends in to the authorities.



I ran part of the way to the bus stop, stopped when I realized I didn't want to get sweaty, then had to run again when I got near the ferry and saw the bus at the far end of the street.  I waved for the bus to stop as it approached and got on.



The bus route I had to take to get to Brian's was kind of a case in point for why my dad wanted to get the ferry going again.  I had to go West, transfer to a different bus, go South a ways, then hop off and walk East for five minutes to get where I wanted to be, the southeast end of downtown, where the office buildings and stores gave way to apartments and condos.



It was a stark contrast to the area where I lived.  It wasn't perfect, honestly, and you could see things like Empire Eighty-Eight's gang tags or broken windows here and there.  Even so, that sort of thing was as rare as finding a house without crap in the yard or a house with stuff obviously broken or run down in my neighborhood. Even the lowest step leading up to the front door of \emph{my} house was rotten out, so I couldn't boast to having one of those nice, not-embarrassing places.  If you fixed it, something else would inevitably break down, so you got used to stuff like the broken step, learned to skip up to the second one, or you entered and left through the back door at the kitchen like I did.



Brockton Bay had originally been a big trading post and port, back when America was being colonized, and some of the buildings were pretty old as a result.  What I saw when I entered the area Brian was staying was a war between the past and the present.  Older buildings had been fixed up and maintained to the point that they were attractive, mostly set up as Victorian style condos.  But where other cities might work to integrate this with the other buildings of downtown, it seemed like the city planner or developers had intended for the inclusion of tall stone or glass buildings to be jarring.  Everything looked \emph{nice, }but it didn't all look nice \emph{together}.



Brian's apartment building was one of the modern ones.  Maybe eight to ten stories tall – I didn't count – it was mostly stone, and there was a floor-to-ceiling window behind each of the balconies.  Two little evergreen trees in pots framed the doorway.  Brian sat beside one of the trees, wearing very similar clothes to the first time I had seen him – a steel blue T-shirt, dark jeans and scuffed boots.  He was leaning back against the wall, his eyes shut, just enjoying the sun.  He'd combed out his cornrows, and his hair was tied back in a long, loose ponytail that sort of poofed out below the elastic.  A bit of hair had slipped out from the elastic and was blowing in the breeze, brushing back and forth against his cheekbone.  He seemed so unbothered by the tickling of the hair that I suspected he might be asleep.



I was surprised he was able to relax like that.  It seemed to me that kicking back like that in any urban area, even a nicer neighborhood downtown, was begging for trouble.  Okay, so maybe there weren't muggings or homeless people hassling bystanders down here, but Empire Eighty-Eight \emph{did} base their main operations somewhere in this general area, and Brian \emph{was} black.



Maybe he could get away with it because he was six feet tall and fit.  Even if you gave me my knife, baton and a good enough reason, I was pretty sure \emph{I} wouldn't want to mess with his nap.



``Sorry to wake you,'' I said, seeing if I could provoke a response.



Even before he opened his eyes, he offered me that wide, genial smile that seemed so out of place on his six foot tall frame.  It was a smile that hid nothing, as honest and unguarded as you'd expect from a ten year old finding out he'd just unwrapped the exact gift he'd wanted for his birthday.



``I wasn't sleeping,'' he got to his feet, ``Figured I'd wait for you here rather than risk you coming and not knowing how to reach me while I was hauling stuff upstairs.''



``Ah.  Thank you.''



``I've still got two pieces of furniture in the car.  Let me grab them and we'll head on up.''  He headed in the direction of a station wagon that was parked in front of the building.



``You have a car?''



``Rental.  Doesn't make sense for me to own a car, especially since half the driving I'd do would be to the hideout.  It'd get stolen, in the first place, and I don't like leaving a license plate number for people to use to track me down, if things go sour.''



I smiled at the word `hideout'.  ``I get it.  Car bad.''



I kicked myself.  Why did I keep lapsing into caveman-speak around him?



He took it in stride, though.  ``Car bad.  Expensive.''



``Says the guy who doesn't sweat paying fifteen dollars for coffee on the Boardwalk.''



``Touche.'' He popped the trunk.  There were two cardboard boxes inside, both just three or four inches thick.  One of them, though, was a square maybe three to four feet across on each side.



``Need a hand?''



``I'll get the boxes,'' he said, bending down to start hauling the largest of the cardboard boxes out of the back.  He stopped to hand me his keys.  ``You close the car door behind me, and get the front door of the building?''



I watched the muscles of his shoulders moving under the fabric of his t-shirt as he lifted the two boxes out of the trunk.  His shoulders were broad, I noticed, but not in the same way you saw with people who exercised just to look buff. That kind of bulk usually looked a little grotesque to me, in a way I couldn't define.  Brian's body was more the product of years of regular exercise with purpose and application.  I looked at the lines of his shoulders and back and, further down, his waist and hips, as if I could make sense of it, define that point where his body was different, where it was more appealing than most.



``Um,'' I said, reminding myself he'd asked me a question, ``Sure.  I'll get the doors.''



Damn it, Lisa, what did you get me thinking about?





