





I opened the glass doors for Brian so he could carry the boxes of furniture in.  The thing that struck me about his apartment building was how uncluttered everything was.  No litter, no people, no noise.  There was a bulletin board just past the second set of doors, which was something I normally might have expected to be a little messy, as a rule, but even there, the individual postings were carefully spaced out, and the entire thing was sealed behind a glass pane with a single small lock.  It felt kind of sterile.  Or maybe that was just me being used to an area with more character.



I didn't know what to say.  Not just in terms of Brian's apartment building – I had no idea what words should be coming out of my mouth.  I didn't have the know-how to naturally make small talk.  I usually got by with constant planning ahead on what I might say.  Problem was, I'd been distracted, not so much by Brian's features, but by the realization that I had been looking at them.  Now that I was trying to recover, get my mental footing and plan out some conversation, all I could think was `Dammit, Taylor, why can't you think of something to say?!'.



We entered the elevator, and Brian rested the boxes on the metal railing on the interior. I managed, ``What floor?''



``Fourth, thanks.''



I hit the button.



We ascended, and as the door opened, I offered Brian a hand in steadying the boxes as he backed out of the elevator.  He led the way down the hall and stopped by a door while I fumbled with the keys he had given me, to find the one to his apartment.



I wasn't sure what I expected to see in Brian's place, but he still managed to surprise me.



The first thing I noticed was that the ceilings were high.  The apartment was virtually two stories, a fairly open concept with few walls.  The kitchen was to our left as we walked in, smallish, separated from the living room by a bar/kitchen counter.  To our right was the hall closet and the walls encompassing the bathroom and one of the bedrooms.  Directly in front of us was the spacious living room, backed by a floor to ceiling window and a glass door leading out onto a stone balcony.  A set of stairs led up to a bedroom set above and on top of the bathroom and first bedroom – I figured that was where Brian slept, going by the not-disheveled-but-not-quite-made bed that was in view from where I stood.



What threw me, I think, was how mellow the place was.  There were two bookshelves, light gray in color, in the living room.  On the shelves, I saw, there was a mix of novels, plants and older books with cracked and frayed leather spines.  The fronds of some of the plants draped down over the shelves below.  The couch and accompanying chair were a pale tan corduroy, oversized with cushions thick and deep enough they looked like you could get lost in them.  I could totally imagine curling up in that armchair with my legs tucked in beside me, a book in my hands.



Somehow I had been expecting aesthetics along the lines of chrome and black leather  Not that I associated Brian's personality or tastes with that sort of design, but it was what I might've thought a young bachelor might go for.  Whether it was the softness of the colors, the little jar with stones, water and bamboo on the kitchen counter or the sepia tone pictures of trees in the front hall, the place gave me a sense of ease.



I felt a pang of envy, and it wasn't just because Brian's apartment was nice.  I was getting a better sense of who he was, and how we were very different people, in a respect.



Brian grunted as he set the boxes down by the front closet.  He pulled off his boots and I took that as my cue to remove my shoes.



``So, I've already got one bit started,'' he told me, leading me into the living room, and I saw that there was a pile of light gray boards and an empty cardboard box leaning against the wall there.  ``Turns out it really needs a second set of hands.  You want anything before we get started?  You prefer tea to coffee, right?  Or do you want a soda?  Bite to eat?''



``I'm fine,'' I smiled, taking off my sweatshirt and putting it down on the kitchen counter.  I'd promised Tattletale I would.  Feeling very self conscious with my belly showing, I tried to distract him with the task at hand, ``Let's get started?''



The first job, the one he'd left incomplete, was a set of shelves, and we started with that.  It was, as he'd said, a job for two people.  The shelves had three columns with six shelves each, and every part interlocked with the help of wooden pegs.  It was impossible to press two pieces near the top together without ones near the bottom pulling apart, and vice versa, so we got into a rhythm where one of us would put pieces together while the other prevented everything else from coming apart.



All in all, it took us twenty minutes or so.  After we verified that everything was fitting together and lined up, Brian hauled the shelf off the floor and set it against the wall.



``That's one,'' he smiled, ``You sure you don't want a drink?''



``What do you have?''



``Here, I've got stuff in the fridge.  Come and take your pick.''



I grabbed a cherry coke.  Brian grabbed a coke, but mostly ignored it while he opened the next box, the square one that was nearly four feet across, and started laying out the individual pieces on the kitchen floor.  A kitchen table with stools.



As it turned out, the kitchen table was a tougher job than the shelving unit.  The legs had to be held at precisely the right angle, or the bolts jammed in the holes, or forced the table leg out of position.  Each time that happened, we wound up having to take the bolt out and start over.  I wound up holding the first table leg steady while he screwed in the bolts at the base.



Without glancing my way, he placed his hand over top of mine to adjust the angle a fraction.  The contact made me feel like someone had plucked a guitar string that ran from the top of my head down through the middle of my body.  A deep thrum deep inside me that couldn't be heard, only felt.  I was very glad for the long sleeves of my top as goosebumps prickled my arms.



I found myself defaulting to my most basic defense, staying quiet, staying still, so I couldn't say or do anything stupid.  Problem was, this made me very, very aware of the silence and lack of conversation.



Brian probably hadn't given the quiet the briefest thought, but I found myself wondering what to say, wondering how to make small talk, or how to get a conversation going.  It was agonizing.



He moved in closer to get a better look as he put a nut on the bolt, and his arm pressed against my shoulder.  Again, it prompted an almost elemental reaction from my body.  Was this intentional?  Was he signalling interest through casual physical contact?  Or was I assigning meaning to something coincidental?



``Nearly done,'' he murmured, adjusting his position to start screwing in the other bolt for the table leg.  His arm wasn't pressing against my shoulder, now, but the way he was crouching, his face was only a few inches from my own.  Okay, that was worse.



``Taylor, you think you can grab that smaller wrench without moving the leg?''



I didn't trust myself to respond without making a funny noise, so I just reached for the little wrench and handed it to him.



``That's faster, thanks,'' he replied, after a second, ``Want to grab me the nut?''



I did, dropping it into his cupped hand rather than placing it there, worried about what I might do or how I'd react if my hand touched his.  I wasn't going to survive the next three table legs like this, let alone the stools or the third piece of furniture we hadn't even started.



``Taylor?'' he asked.



He let the question hang, so I swallowed and replied, ``What?''



``Relax.  You're allowed to breathe.''



I laughed lightly at the realization I was holding my breath, which resulted in a nervous, chuckling exhalation that only added to the awkwardness I was feeling.



He was smiling, ``You okay?''



What was I supposed to say?  Admit I didn't know how to deal with being around a good looking guy?



I stared down at the ground, at the table leg I was holding.  ``I get nervous when I'm close to people.  I think, you know, maybe I have bad breath, or maybe I have B.O., and I wouldn't be able to tell, because it's mine, so I hold my breath like that to be safe.  I dunno.''



Bravo, Taylor.  \emph{Bravo}.  I imagined the slowest, most sarcastic of slow claps.  Talking about bad breath and B.O. was \emph{totally} the way to go.  One of those brilliant moments that would have me cringing every time I remembered it in the next few years or decades, I was sure.



Then Brian leaned close, closing the scant inches of distance that separated us, until our noses were practically touching.



``Nope.  You smell nice,'' he told me.



If I'd been a cartoon character, I was pretty sure that was the point where I'd have steam shooting out of my ears, or I'd be melting into a puddle.  Instead, I went with my first instinct, once more, and went very still.  I became aware of a heat on my face that must have been a furious blushing.



It would be hard to say whether it was a mercy or not, but Brian was distracted by the sound of a key in a lock, and the opening of the front door.



My first thought was that the girl who walked in was Brian's girlfriend.  Then I saw her glance our way, smirk, and noted the similarity between her eyes and Brian's.  His sister.



My second thought, or my second response, really, was hard to put into words.  It's like, you could look at a Mercedes, and say that it was a beautiful work of art, even if you weren't someone who paid much attention to cars.  Along similar lines, when you saw a Mercedes with a cheap flame decal pasted around the wheels, and a tacky homemade spoiler stuck on the back, it was painful and disappointing on a fundamental level.  That was what I felt, looking at Aisha.



She was beautiful, as feminine as Brian was masculine, with high cheekbones, a long neck and even though she was two or three years younger than me, she already had breasts larger than mine.  I could be convinced to chop off a finger for legs, a waist and hips like hers.



Damn, this family had good genes.



You just needed one look at Aisha to know that she was going to be drop dead gorgeous when she had finished growing up.  All that said, though, she had a streak of hair bleached and some of that bleached hair had been dyed into a stripe of purple.  It was as though she had gone out of her way to look trashy, with ripped denim shorts over neon green fishnet leggings, and a strapless top I would hesitate to even call underwear.  Any envy I felt towards her was accented by an almost offended feeling, as far as how she was spoiling what she'd been naturally given.



``Am I interrupting?'' she said, her tone vaguely mocking, as she gave me a look I couldn't quite figure out.



``Aisha,'' Brian stood up, ``What are you doing here?  You--'' he stopped as a solid, heavyset black woman entered through the front door.  Where Aisha's glance my way had been ambiguous, the look this woman gave me was anything but.  Disapproval, dislike.  I realized what I must look like, slightly sweaty, on the floor amid pieces of furniture, stomach showing, practically glowing with a pink blush.  I hurried to grab my sweatshirt and pull it on.



``Mr. Laborn?'' the heavy woman said, ``I'm afraid I expected you to be more prepared, but it seems like you're in the middle of something.''



Brian shook his head, ``Ma'am.  Mrs. Henderson.  I'm almost positive your office told me to expect you at two this afternoon.''



``That was the original time.  Aisha told me you wanted to reschedule--'' Mrs. Henderson trailed off and gave Aisha a hard look.



Aisha smiled, shrugged, and hopped up so she was sitting on the end of the kitchen counter.  ``What?  There's a movie I want to see this afternoon with my friends.''



``If you'd asked, I might have said yes,'' Brian told her, ``Now I'm probably going to say no.''



``Not your call, bro, I'm not living with you yet,'' she raised a double-set of middle fingers his way.



Brian looked like he was going to say something else, but then he stopped himself.  He sighed, then turned his attention to Aisha's caseworker, ``I'm sorry about this.''



She frowned, ``Me too.  I should have called to check, given Aisha's history of bending the truth.''  She looked at her notebook and turned a page, ``If you'd like to reschedule, hmmm, I'm afraid I've already filled the afternoon slot, but perhaps this weekend\ldots?''



Brian gave Aisha an annoyed look, ``Since you're already here, if you're willing to look past the furniture we haven't finished putting together, we could do it now.''



``If you're sure?  What about your\ldots companion?'' she glanced at me.



My blush probably hadn't gone away, and I suspect I blushed a little harder at suddenly being put in the middle of an awkward situation.  Probably didn't help banish any wrong impressions she'd picked up.



``She's a friend, she was helping me out.  Taylor, I'm not sure how long this will be.  I don't want to waste your time, but I'd feel bad if you left so soon after coming all the way here.  If you want to stick around and take it easy, I could give you a ride back after.''



Every socially awkward part of my brain itched to take the offered escape route, make my exit, cool off.  It was hard to say why I didn't.



``I'll stay, if I won't be in the way.  No plans for the afternoon.''



When Brian smiled, I realized why I hadn't jumped on the chance to leave.



The woman gave me another close examination.  She asked me, ``Are you in his online class?''



I shook my head.



``No.  You looked a little young for it.''  Then she challenged me, ``Why aren't you in school?''



``Um,'' I hesitated.  Stick as close to the truth as possible.  ``I was caught at the edge of one of the bomb blasts, got a concussion.  I'm missing classes until I'm totally better.''



``I see.  I'm sure that assembling furniture is what the doctor intended when he told you to rest and recuperate?''



I smiled awkwardly and shrugged.  Man, I was really hoping I wasn't tanking this thing for Brian.



``So,'' Brian spoke to Mrs. Henderson,  ``You wanted to look my place over, and see the space I set aside for Aisha?  I guess this is a chance for you to check out a place before the family has scrambled to sweep everything under the rug.''



``Mmm.''  A noncommital response.  ``Let's step onto the balcony, and you can tell me about the area and the nearby schools.''



Brian led the way and held the door for the caseworker.  It swung shut behind him, leaving me with Aisha, who was still sitting on the kitchen counter.  I gave her a small smile, and received a cool, penetrating stare in return.  Uncomfortable, I turned my attention to the table and tried to see what I could do on my own, with the second leg.



``So.  You're on my brother's team?''



What?  I was proud of myself when I barely missed a beat.  ``Team?  I know he boxes, or boxed, at least, but--''



She gave me a funny look, ``You're going to play dumb, hunh?''



``I'm not following.  Sorry.''



``Right.''  She leaned back and kicked her legs a bit.



I turned my focus back to the table leg.  I didn't get very far before she interrupted me again.



``Look, I know you're on his team.  Process of elimination, you have to be the bug girl.''



I shook my head, as much to deny it as in exasperation.  What the hell, Brian?



``He told me that he had powers, didn't say what they were.  Since he has powers, he thinks there's a chance I could get 'em too.  Didn't want me to be surprised.  I figured out who he was after that, saw something about some villains robbing a casino on a night he wasn't at home, started keeping track of times he wasn't available and it kept matching up.  Called him on it, and he didn't do a very good job at denying it.''



Hoping to throw her off balance, I put the most convincing wide eyed expression of shock on my face that I could manage, ``You're saying your brother's a \emph{supervillain?}''



She blinked twice, then said, slowly, like she was talking to someone with a mental handicap, ``Yeaaaaah.  And I'm saying you are, too.  Why else would my brother be hanging out with you?''



Ouch.  That stung.



I was spared having to come up with a response and keep the charade going when Brian and the caseworker came back from the balcony.



The caseworker was saying, ``\ldots{}hesitant, with the waiting list.''



``She's in the territory and she'd be entering the school at the same time as the rest of the grade nine students.'' Brian replied, giving Aisha the evil eye, ``And it would mean separating her from the bad influences around where she's living now.''



Aisha gave him the finger, again.



``Mmm,'' the caseworker replied, glancing from Aisha to him. ``I'd like to see your bedroom next?''



``Mine?  Not Aisha's?''



``Please.''



Brian led the caseworker up the stairs to his bedroom, which overlooked the rest of the apartment.



``Maybe I should see how you react if I shout it aloud,'' Aisha suggested.  She played up an accent, ``What do you call yourself, again?''



I rolled my eyes.



``Not saying?  Whatever.''  Hands cupped around her mouth as though she were shouting, she mock-shouted at a volume barely above regular speech, ``Ladybug and Grue, in da house!''



I glanced upstairs, hoping that Brian and the caseworker weren't in earshot.  The murmur of conversation up there didn't seem to have been interrupted by what Aisha had said.



``Seems like you'd be in a lose-lose situation, broadcasting it like that,'' I replied, ``Either you're right, and you tick off two people you really might want to avoid angering, or you're wrong and you look crazy.''



``What if they already think I'm a little crazy, though?  What do I have to lose?''



``Can't say.''  I tightened the bolt, checked the chair leg, and found it solid as a rock.  I moved on to the next one.  ``What do you have to gain?''



``Come onnnn,'' she wheedled, ``Just admit it.''



My heart was pounding when Brian and the caseworker came down the stairs.  Aisha, for her part, pasted a wide, fake grin on her face to greet them.  Brian ushered the woman into the second bedroom, but didn't go inside with her.  He stopped to look at me.



``Taylor, you don't need to do that on your own.''



``It's alright,'' I said.  Glancing up at where Aisha was sitting on the countertop, I added, ``It's a nice distraction.



``Sorry.  I think we'll be just another minute.''



It was, it turned out.  The caseworker exited Aisha's bedroom-to-be and glanced through the bathroom, then investigated the cupboards and fridge.



Mrs. Henderson spoke to Aisha, ``I'd like you to step onto the balcony for a minute.''



``Whatever.''  Aisha hopped down from the counter and headed outside.



``And,'' she said, turning to Brian, ``You might want your \emph{friend} to step outside too.''



``I don't really have anything to hide,'' he answered, glancing my way.



``Alright.  Let me start off by saying this is better than most.''



``Thank you.''



``But I have concerns.''



You could see Brian's expression change a fraction, at that.



``I read the documents and plans you emailed me.  You have a solid plan in mind for accounting, paying the bills, assisting with her education, possible extra expenses, clothes budget, even setting money aside for college.  In many respects, this is the sort of situation I wish for, with most of my cases.''



``But?''



``But when I look at this place, I see that you've made it very much \emph{yours}.  The furniture, the decorations, the artwork, they seem to point to your personality, leaving very little room for Aisha's, even in the space you've set aside for her.''



Brian looked a little stunned at that.  ``I see.''



``Look, Mr. Laborn, we have to consider Aisha's perspective.  She's a serial runaway.  She clearly doesn't see your father's place as a home.  Extra care should be given to ensure she sees \emph{this} as one.  Assuming she winds up here and not at her mother's.''



``My mother's,'' Brian's expression took on a more serious cast.



``I'm aware of your concerns on the subject of Aisha's mother, Mr. Laborn.''



My cell phone buzzed once in my sweatshirt pocket.  I ignored it.



Brian sighed, sagging a little, ``Is this fixable?''



``Yes.  Involve Aisha in the decoration, be willing to compromise your tastes and aesthetics to allow her to feel like this is her space too,'' she said, ``I know it won't be easy.  Aisha is difficult sometimes, I'm sure we can both agree.''



I was beginning to gravitate towards that conclusion, myself.



``Yeah,'' Brian nodded, ``So what's next?''



``I'll be making a visit to her mother's home in a week and a half, if I'm remembering right.  If you want to send me another email when you feel you've amended this minor problem, and the small handful of things I pointed out during the inspection, I could arrange to stop by again.''



``That would be terrific.''



``Keep in mind that I have an overflowing caseload, and I probably won't be able to stop by until at least a week after you've let me know.''



``Thank you,'' Brian said.



``Any questions?''



He shook his head.



``Then I wish you luck.  To apologize for the unexpected appointment time, I'll make you a one time offer to take Aisha off your hands.  If she insists on getting herself suspended, I can maybe introduce her to some other that went down that road, while I go to this afternoon's appointments.''



Brian smiled.  Not quite that amazing smile I'd seen so often, but a nice smile nonetheless, ``I guess she'll be missing that movie she wanted to go to.''



``Looks like,'' the caseworker smiled conspiratorially.  ``Keep it up, Mr. Laborn.  Aisha's lucky to have you.''



Brian perked up a little at that.



The meeting didn't last long after that, and a complaining Aisha was dragged off by the caseworker.  I couldn't quite breathe a sigh of relief until they were gone.  Even then, I was uneasy, knowing how strong Aisha's suspicions had been.



Remembering that my phone had buzzed, I reached for my cell phone to see what the message had been.  While holding down the button to unlock it, I told Brian, ``Aisha knows about the Undersiders, looks like.''



``Shit.  Sorry,'' he made a pained face, ``If I thought you'd be running into her, I would've given you a heads up.  You didn't say anything?''



``Pretended not to know what the hell she was talking about, for all the good it did.  Is this going to be a problem?''



``She promised she wouldn't say anything to anyone\ldots and it really bothers me that she was indiscreet enough to raise the subject with someone I hadn't okayed.  But Aisha wouldn't tell for the sake of telling.  I think she was probably messing with you.''



``If you're sure,'' I had my reservations, but I wasn't sure I wanted to press him on the subject, when he was already stressed.



``Pretty sure,'' he sighed.



I looked at my cell phone.  It was from Lisa.



\msgbox{srry to interrupt smoochfest. you two need to hurry back.  shit is going down.}



I felt a bit of heat on my cheeks as I took extra care to delete the text.  When I was done, I turned to Brian.  ``Lisa says something's up.  She says to hurry back.''



``Pain in the ass,'' Brian said.  ``I was hoping\ldots ah hell.  Guess we're not going to get this stuff put together, huh?'' he smiled at me.



I smiled back, ``Another time.''



He gave me a hand to help me to my feet.  Was I being hopeful or observant when I noted his hand maybe lingered a half second longer than necessary on my own?



Was a part of me dreading those possibilities, hoping that it was neither hope nor accurate observation on my part?  Because I couldn't quite tell if there was, or if I just wanted there to be a sane part of me having a say.



Fuck.  I mentally moved up my timeline.  No longer than a week, and I'd have to take what I knew about the Undersiders to the Protectorate.  I wasn't sure I trusted myself for any longer than that.

