





``Thanks to a concerted effort by members of Brockton Bay's Wards and Protectorate teams, the local gang, the `ABB', or Azn Bad Boys, has fallen.''



Brian and I had arrived at the loft just in time to catch the bulletin on the news.  Lisa, Alec, Bitch and the three dogs were gathered on the couches.



``The heroes of the hour are the young members of the Wards, Clockblocker and Vista, who played a pivotal role in managing a crisis with a \emph{superbomb}, allegedly used by the supervillain Bakuda in an attempt to hold the city ransom and guarantee her safety.  While experts on the scene refused to offer hard numbers, a local cape was quoted as stating the superbomb could have had a yield of nine thousand kilotons of energy.  This device, containing power on par with conventional nuclear bombs, was fashioned with household materials scavenged from the area, after fighting in the Docks and pressure from local authorities forced the bomb's alleged creator to relocate to a derelict boathouse just days ago.  Were it not for the efforts of the Wards, this might have been a tragic day for our nation.



``As much as we might wish for a period of somber reflection, other local villains have shown little interest in putting recent matters to rest.  Less than an hour after suspected ABB leader Lung and alleged accomplice Bakuda were brought into custody, the head offices of Medhall Corporation were assaulted by armed forces, in an altercation that drew the attention of members of local Aryan villain group Empire Eighty-Eight.  This appears to have prompted a rash of more than six major incidents in the past hour-''



Lisa muted the TV, turning around on the couch to look at Brian and me.  ``I'll give you the cliff notes.  The Travelers just hit an art gallery and an airport in the span of an hour.  Coil and Empire Eighty Eight are apparently trying to make up for lost time and are just a hair away from open warfare on the streets.  The Merchants – Skidmark's group – are taking advantage of the chaos and trying to do what the ABB did, but with local drugheads and hobos and zero control over their situation\ldots they won't get far, but I'm sure they're having a grand old looting spree.''



``So the ceasefire is over,'' I spoke.  Weren't things supposed to get \emph{better} with the ABB gone?  Why did I feel partially responsible for this?



``It's like everyone was poised at the starting line, ready to move the instant the gun fired,'' Alec said.



``Except us,'' Brian pointed out.



``Not necessarily,'' Lisa shook her head, ``Five minutes after Medhall got hit, we got a message from the boss.  He's got a job he wants us to do, maybe our biggest yet, but the timeline's short.  It's why I called you here.''



Brian folded his arms.



``Here's the thing,'' she said, ``Morale is down.  The city is spooked, and things aren't calming down the way people were hoping they would.  The fact that we all dodged a bullet with this superbomb thing?  It didn't help.''



She typed on her laptop while she talked, ``Topping it off, it doesn't look good when the local news gets wind of the fact that a large part of the fighting against the ABB was being done by villains.  Get my drift?  So with the idea that they were planning a fundraiser around now anyways, the mayor's promoting a function to help sell the idea that it was the good guys that were the major players here.  End result?  A fundraiser-slash-celebration involving the Protectorate, Wards, the PRT forces, cops and all those guys.  Tonight.  Most of the Wards and New Wave are gonna pick up the slack in the meantime, to keep the city protected, because the mayor's prioritizing PR here.''



``I'm not liking the direction this is going, here,'' I told her.



She picked up her laptop and set it on the back of the couch, facing me and Brian.  The page showed details on the celebration, had links to ticket vendors and sported an image of a bunch of people in tuxedos and gowns.   ``The Protectorate and some of the Wards are going to be there with the upper crust of Brockton Bay, their friends and family, and anyone else willing to shell out the cash for a ticket.  The boss wants us to, quote, 'embarrass them', unquote.''



There was something of a stunned silence.  I glanced at Bitch and Alec, and gathered from their expressions that they had already heard this.  In contrast to the situation we'd had with the bank robbery, though, they didn't look all that keen.



Brian started chuckling.  After a bit, his chuckle became an all-out laugh.



I didn't wait for him to finish before I said my piece, ``Are you insane?  You want us to, what, crash a party, fuck with the people there and then scram before we get ourselves arrested by the-'' I struggled to find the words, ``By half the fucking heroes in Brockton Bay?!''



``Basically.''  Lisa said, raising her hands as if to get me to calm down, ``Though it's probably more like a third of the city's heroes.''



``Right,'' I said, ``No offense, Lisa, I'm fond of you and everything, but you kind of underestimated the number of heroes that would show up to the bank robbery, too.  Don't forget that a bunch of heroes came from out of town to help with the ABB situation, and they might stick around for the after-party.''



``True,'' she admitted, ``But still-''



``And the plan is to piss them off?'' I asked, incredulous, ``Not just them, either, but that party's probably going to be attended by the mayor, the DA, the police chief\ldots You're aware that if we tried this and any of us got caught, it would pretty much be a first class trip to the Birdcage?''



``Sorry, Lise, this is a no,'' Brian told her, still looking amused, ``I'm perfectly cool with letting all the other groups go at it for a bit.  We did our part, and we've got nothing to lose in kicking back for a little while.''



``Yeah.  I don't get the point,'' Bitch said, scratching the top of Brutus' head.



``You won't find anyone more willing to get a little crazy than me,'' Alec told Lisa, ``But I'm with Bitch.  It's a whole lot of risk, a whole lot of trouble.  For what?  Tweaking the good guys' noses?''



``The boss is willing to pay,'' Lisa said.  ``With other considerations.''



``Considerations?'' I asked.



``You have to understand,'' Lisa sighed, ``I don't disagree with what you guys are saying, but what I can tell you is that this is a test.  The boss wants to see if we can pull this off, and if we can, we're that much more valuable to him.  A lot more valuable.''



``Or maybe the test is whether we're smart enough to turn down a doomed mission,'' Brian pointed out.



``Maybe,'' Lisa conceded, ``I don't think so, but I won't deny that it's possible.''



Brian asked her, ``\emph{Can} we turn this down?  I mean, he's never forced us to take a job.''



``We could,'' she didn't look happy.



He frowned, ``I think it's four votes against, at the very least.  I'm assuming you're going to vote for this plan, Lise?''



``Yeah,'' she replied.



``Well, unless we've switched from a majority vote system, I guess you can tell the boss `thank you, but no','' he said.  When she didn't reply, he turned to me, ``Want to see about putting that kitchen table and bedside table together?  I can treat you to a late lunch, if-''



``Two hundred and fifty!'' Lisa interrupted him.



He gave her a look, ``Two hundred and fifty\ldots''



``Thousand,'' she finished for him, dropping her arms to her side, almost defeated.  ``Each.  Damn it.  I wanted to get you guys on board before I wowed you with the amount.  Sounds desperate when I say it like this, but I can't let you walk away without letting you know what we'd be turning down.''



The sum gave us pause.



``Just to be clear\ldots One million, two hundred and fifty thousand dollars, divided five ways,'' Alec said, ``For this?''



``Like I said,'' Lisa smiled a little, ``Biggest job yet.''



``If the boss offered us a quarter million dollars each to walk up to those guys and turn ourselves in, it wouldn't be that different a scenario,'' I pointed out.



``Sure it would,'' Lisa retorted, ``We actually have a chance at getting through this, free and clear.''



``A very, very small chance,'' I pointed out.



``A chance,'' she said.  ``But if we do this?  If we prove to the boss that we're worth his while?  We move up.  We get more money, we get more equipment, information, we get a voice as far as shaping his long term plans, all of which may translate to more respect in the cape community.''



``A voice?'' I asked, ``What do you mean?''



``Meeting with him, discussing what we do next, and why.''



My mind started racing with the implications of this.



``I'm changing my vote,'' Alec said, ``This much money, it sort of solves the problem I had with the job, which was that it was sort of pointless.  A quarter million dollars is pretty pointy.''



``Two for, three against,'' Lisa said.  ``Bitch?''



Bitch scowled, ``Let me think.''



This was a chance to meet our employer, in the not too distant future.  Question was – did I want to take it?  I'd been procrastinating, avoiding the issue, trying not to think too much about my game plan, about turning these guys in when I had the last bit of information I needed about how they ran things, about where the money came from.  Now I had to make a call.



All along, I'd been telling myself that I'd turn them in.  Give the information to the Protectorate.  But my heart wasn't really in it.  It would mean turning on friends.  While I didn't dislike Alec or even Bitch, my thoughts were on Lisa and Brian.  I mean, well, Lisa was my first real friend since Emma.  As for Brian, I liked him, respected him.   I hated the idea of doing to them what Emma had done to me.  Betraying friends.



I'd given up the idea of gaining respect or prestige for turning them in.  I mean, I'd committed a felony, taken hostages, attacked other heroes, nearly killed a man, then carved that same person's eyes out a couple of weeks afterward.



And I could live with that part, with not getting credit or accolades or whatever.  I could see myself flying under the radar for a while.  Perhaps playing the role of a vigilante avoiding the attention of both hero and villain, if I was really itching to get out in costume.  Or see if maybe, just maybe, I could try for the same deal that Shadow Stalker got, become a probationary member of the Wards.  I'd initially veered away from the Wards out of concern that it would be too similar to high school\ldots but I'd changed in the past few weeks.  Stood up to Emma twice.  Three times, if you counted the meeting.  I had a little more backbone than I'd had a month ago.  I could picture myself laboring alongside a group of junior superheroes that resented me as a kind of penance for my villainous actions, and that was a pretty big change from before I'd even gone out in costume, when the very idea of joining them was hard to process.



The problem was, going down that road was a mess of maybes and possiblies, each step a mess of potential disasters.  What if I got arrested rather than offered probationary membership in the Wards?  What if the Undersiders escaped arrest and came after me?  Or my dad?



It came down to the people that were in the room with me.  It wasn't just that I would be betraying them like Emma did to me.  Was I brave enough to go through what I had with Emma, with having people I liked and looked up to becoming my worst enemies?



And if I didn't choose, didn't decide\ldots Well, if I put it off any longer, the only difference from staying for good by choice would be a fair sized measure of self delusion on my part.  The time I'd spent with Brian made that clear enough.



``I think\ldots I might change my vote,'' I voiced the thought aloud as I formed it.



There were looks of surprise from everyone present, excepting the dogs.  Lisa, especially, rocked back a little in reaction to my statement.



It took all I had to keep my facade intact.  At the end of the day, what scared me more than losing friends and having them hate me, more than having them come after me or my dad, was the idea that I would hate myself.  That I would hate myself one, five, ten or twenty years down the line, for betraying my principles and for making a bad call with wide reaching implications.  Hate myself for taking a road that might lead me going to jail with no chance of getting bailed out by Armsmaster, or going down a path that led to me hurting someone innocent as badly as I'd hurt Lung and Bakuda.



Sticking with the Undersiders was a short term gain, sure, but long term?  I had to stick with my original plan, and try to convince myself I was doing it for the greater good.



Alec raised his eyebrows.  ``Really.''



``What?'' I asked.



``You're the last person I would have expected to change your vote, dork,'' he said, ``You're careful, and this is the least careful job we've had yet.''



``Changing my vote is provisional on whether we can come up with a plan that has a decent chance of us escaping with our skin intact,'' I clarified.



``Still, you're usually Brian's shadow, echoing him,'' Alec said.



``Thanks, Alec,'' Brian frowned.  Brian turned to me, his eyebrows knitting together in concern, ``You sure?''



``Not totally,'' I admitted, ``And I'm sorry, for not backing you up.''



``You're a member of the team, you're allowed your own voice.''



``What changed your mind?'' The question came from Lisa.



I had to avoid tripping any alarms with her.  The safest way to go about it would be to stick with the truth, or something very close to it.



``It bugs me that I don't know who our employer is.  There's some real ugly possibilities, and I'd rather know sooner than later, if they were the case.''  There, truth enough.



``I admit,'' Brian conceded, ``I \emph{am} curious.  It's\ldots I don't think I'm curious enough to want to take this job.''



``If the scrawny kid is gonna do this, I'm not backing down,'' Bitch said.  ``I'll change my vote too.''



``Kid?'' I asked her, ``Scrawny, sure, but I'm probably a year younger than you, at most.''



Lisa stopped us, leaning to one side to put herself between Bitch and I.  ``We have to stay on topic, since there's only a few hours to plan and get ready.  We have four votes for, one against.  Looks like this is gonna happen.''



Brian sighed.



``Sorry,'' I murmured my second apology.



He put his hand on my shoulder, ``It's okay.''



I noticed he didn't move his hand off my shoulder right away.



Distracting myself, I asked Lisa, ``So how do we pull this off?''



She began outlining a plan.





