





My legs hugged the sides of Judas' body.  I could feel his breathing beneath me, the expansion of his body as his lungs filled, then emptied.  He huffed out a breath, and it steamed in the cool night air.



He stepped forward, just a little, and I got a glimpse of the world below us.  Thirty two stories down, the cars on the street were visible only by the yellow and red points of their headlights and taillights.  I felt Tattletale clutch me tighter, from where she sat behind me.  Judas' front paw rested on the stone railing of the rooftop, clutched it hard enough that the points of his nails bit into the concrete.



Getting up here had been easy enough – Tattletale had cracked the employee access door and we'd taken the supply elevator to the roof.  Had someone been alerted to our presence?  Spotted us on camera?  Hard to say.  But time was short, and we'd already wasted enough time waiting for the dogs to finish growing.  The moment Bitch deemed them set, we would move out.



This plan had been terrifying when we'd just been talking about it.  Actually being on the verge of doing it?  Ten times worse.



\emph{Still time to think of a reason to back out.}



Bitch's whistle, one of those ones that make you wince when you hear them a hundred feet away, cut through the faint, ambient hum of the city below us.



\emph{Last chance, Taylor}.



A second later, Brutus, with Bitch and Grue astride his back, stepped over the edge of the roof.  Judas shifted forward under me, then followed.



Falling from a height like that, you don't get to scream.  The wind takes your voice from you.  If you happen to have something to hold onto, you cling to that for dear life and you pray, even if you aren't a praying type.  My hands clutched hooks of bone on either side of Judas' neck hard enough that I thought I might break either the bone or my hands.



Three stories down from the roof, there was a patio.  As Bitch whistled and pointed from her position below us, Judas kicked against the wall just behind us, pushing out and away from the building.  My heart rose into my throat and stuck there as I saw the edge of the patio below us, surely out of reach.  Had he pushed too early?  The next chance we'd have to touch a surface would be when we spattered violently against the road.



His instincts seemed to be better than mine.  His front claws reached down and gripped the patio's edge.  Every muscle in my body tensed in my effort to not be thrown off him as we stopped, even with his powerful body absorbing the worst of the fall.  He gripped the ledge, then pushed against it while leveraging his back legs into place.  With every muscle in his body, it seemed, he leaped.  Not down, this time, but out.



Time seemed to stand still as we left the building behind.  The only thing below us was the street, twenty-nine stories below. The wind blew through my hair with a painful bite of cold. We'd crossed the event horizon, it was do or die from here on out.  That made it eerily easy to cast aside all doubts and hesitation and steel myself for what came next.



The Forsberg Gallery was twenty six stories tall and was one of the more recognizable buildings you could find downtown.  If I remembered right, it had been designed by Architecture students at the university, a few years ago.  I wasn't really a fan of the design, which resembled the late stages of a game of Jenga, with each section formed in tempered glass with steel bars and girders providing the base skeleton.  The entire thing was illuminated by lights that changed according to the time of the evening.



In the blue-gray of the evening, the tower was pink and orange, echoing the sunset that had finished just an hour ago.  As the leap carried us over it, a pink tinted spotlight consumed my vision.



My lenses absorbed the worst of the glare, and a second later, I was able to make out what was happening again.  Brutus, a matter of feet in front of us, slammed into the glass of the roof, sending cracks spiderwebbing across it.  Grue virtually bounced from where he sat on Brutus' back, losing his seat, hit the glass of the roof with his shoulder, and began to slide.  There was barely any traction to be had, not even on the steel girder that separated the massive panes of glass, and the only thing at the end of that slide would be a very long fall.



He reached out and grabbed ahold of the end of Brutus' tail, pulling himself to a standing position at the same moment that Judas, Tattletale and I crashed into the pane of glass to their right.



The damage Brutus had done on impact was enough to ensure that we could \emph{break through} rather than simply breaking the window.  There was a moment where you could hear the sound of straining metal, followed by the sound of a \emph{lot} of shattering glass.



Together we all dropped into the center of the Forsberg Gallery's top floor, joined by a downpour of glass shards.  Grue landed on his feet and stumbled back as Brutus landed just in front of him.  All around us, there were people in fancy dress and uniforms.  Suits, dresses\ldots costumes.  People ran screaming and running for cover.  Heroes stepped forward, some trying to grasp the situation in the midst of the chaos, others putting themselves between us and the civilians.



A matter of heartbeats after we touched ground, Regent and Angelica plunged into the room, landing just behind us.  Regent lost his seat as Angelica landed, but managed to roll as he hit the ground, bringing himself to a crouch as he stopped.  He \emph{almost }managed to make it look intentional.  Angelica stepped up to Bitch's side, wearing the same harness we'd fitted her with at the bank robbery, but with two large cardboard boxes strapped to her sides, rather than bags.



I felt weirdly calm as my eyes swept over the room.  The Protectorate was gathered around the stage at the back of the room.  Armsmaster, Miss Militia, Assault, Battery, Velocity and Triumph.  Dauntless was MIA.



Not far away was the `kids' table with some of the heroes of the hour.  Clockblocker, Vista, Gallant and Shadow Stalker, interrupted from their mingling with the rich kids, teen actors and the sons and daughters of the local who's who.  The platinum blonde in the white evening gown that was giving me the evil eye?  That would be Glory Girl, out of costume.



Standing guard by the front of the room, raising their weapons in our direction, was an on-duty PRT squad.  Their very recognizable uniforms were chain mesh augmented with kevlar, topped with faceless helmets.  The only means you had to identify them with were the badge numbers printed across their vests in bold white numbers.   Four of the five had what looked like flamethrowers.  They weren't firing yet – they couldn't.  They were packing the best in nonlethal weaponry, but there were elderly people and children in the crowd, and according to Tattletale, that meant they were prohibited from opening fire on us for the moment.



The civilians\ldots men and women in their finest clothes and jewelry.  A combination of the richest and most powerful people in the city, their guests and those willing to pay the exorbitant prices for the tickets.  The tickets started at two hundred and thirty dollars and had climbed steeply as they'd been bought up.  We'd initially considered attending as guests, for one plan of attack, before we decided that it was too dangerous to risk having our secret identities caught on camera, or to have something go wrong as we attempted to smuggle our equipment, costumes and dogs inside.  Once we'd decided that much, we'd stopped checking the cost of tickets, which had gotten as high as four hundred dollars a person.  The guests could use thirty dollars of the ticket price to bid on an auction, but it was still pretty exorbitant.



I recognized the mayor – the first time I'd seen him in person.  There was a guy who might have been a lesser known actor – I thought I recognized him, too.  The rest were just people, maybe a bit better looking than the norm, a bit better dressed.



And Emma.



I could have laughed.  She was standing there in the crowd with her parents and older sister, looking scared shitless in a little sky blue dress and blue sandals. Her dad was a high profile divorce lawyer.  I supposed it was possible he'd worked for someone famous or powerful enough that his family hadn't needed an invitation or expensive tickets to get in.



It kind of sucked, knowing I was about to give her an awesome story to share with the rest of the school when her suspension was over with.  I was really, really hoping it wouldn't be a story along the lines of `these idiotic villains just pulled a stunt so dumb it would put \"{U}ber and Leet to shame, and got themselves arrested in a matter of seconds'.



Tattletale laughed, with a nervous edge, ``Holy shit!  Not doing that again!  Fucking intense\ldots'' Her voice trailed off as Grue blacked out the crowd, leaving only the spot where we stood and the very edges of the room clear of the darkness.  She gave him a dirty look.



``Bitch, Regent, go!'' He shouted, as he stepped my way, grabbed my hand and practically pulled me from where I sat on Judas' back.  Tattletale hopped down, following a pace or two behind us.



The three of us ran for the front of the room, while Bitch whistled for her dogs and ran for the back.  I sensed it when Regent unhitched the two boxes that were strapped to Angelica.  The boxes were heavy and  hit the ground hard, splitting at the seams.  Better than I'd hoped.  I had my bugs flow out from the top of the box and the split sides, and ordered them into the crowd.



If a few more of the biting and stinging sort headed in Emma's general direction, it wasn't due to a \emph{conscious} choice on my part.



If everything went according to plan, Bitch, Regent and the dogs could delay or stop anyone who ventured beyond the cloud of darkness.  Everything else, our success or our humiliating arrest, hinged on Grue, Tattletale and I.



My bugs reached the front of the room just seconds before we did.  I could sense their locations, and this in turn gave me the ability to identify where the people, the walls, doorway and furniture were.



I was moving with my knife drawn before Grue even banished some of his darkness to reveal a portion of the PRT squad that was stationed at the entrance.  As the cloud of black dissipated into tendrils of smoke, I was stepping behind one of the team members, drawing my knife against the hose that extended between the flamethrower-like device he held in his hands and the tank on his back.  It didn't cut immediately, forcing me to try a second time.  As the knife severed the material of the hose, the PRT team member noticed me and drove his elbow into my face.  My mask took the worst of the hit, but getting hit in the face by a full grown man isn't any fun with any amount of protective headwear.



I fell back through the doorway even as the tank began emptying its contents onto the floor.  It was a yellow-white, and as it poured onto the ground, it expanded like shaving cream.  The tank was probably close to three gallons, making for a hell of a lot of foam.



Grue leveraged all of his weight to bodily kick one of the squad members into the foam, then slammed the base of his palm into the next guy's chin.  As the man reeled, Grue grabbed at the tank on his back and pulled it up over his head.  This not only pulled the man off balance, but the weight of the tank kept him that way.  Grue, his hands still on the tank, pulled the squad member's helmeted face down at the same time he brought his knee up.  The pane of the helmet cracked, and the man didn't even have the wherewithal to bring his hands up to soften the fall before hitting the ground.



A fourth squad member stepped out of the darkness, and Tattletale took hold of the nozzle of the man's weapon, forcing it to one side before he could open fire.  I scrambled to my feet to help her.  As Tattletale began to lose the wrestling match over the weapon, I leaped over the still-expanding pile of foam, then went low as I landed to knock his legs out from under him.  He fell, hard, and Tattletale wrenched the weapon from his hands.  As he climbed to his feet, she pulled the trigger and blasted him in the face.  Grue banished enough darkness to reveal the final member of the team, and Tattletale buried him under a blasting of the foam.



I'd watched a discovery channel feature on this stuff.  The PRT, the Parahuman Response Team, was equipped with tinker-designed nonlethal weaponry to subdue supervillains.  This containment foam was standard issue.  It ejected as a liquid, then expanded into a sticky foam with a few handy properties.  It was flexible and it was porous when fully expanded, for one thing, so you could breathe while contained within it, at least long enough for rescue teams with a dissolving agent to get to you.  It was also impact resistant, so PRT squads could coat the ground with it to save falling individuals or keep heavy hitters from doing much damage.



The way it expanded, you could coat all but the strongest villains in it, and it would disable them.  Because of the way it denied you leverage and was resistant to impacts and tearing, even the likes of Lung would have trouble pulling themselves free.  Topping it all off, it was resistant to high temperatures and a strong insulator, so it served to handle the pyrokinetics and those with electromagnetic powers.



While the PRT member struggled ineffectually to remove his foam-covered helmet, I pulled the tank off him and helped Tattletale put it on.  Grue already had his on, and was getting a third one off one of the foam-captured PRT team members for me.



It was heavy, and I almost couldn't handle the weight.  Rather than stagger around, I crouched and let the base of the tank rest against the ground.



Grue pointed to our left, and we aimed.  A second later, he made the darkness dissipate, showing the buffet table surrounded by the various Wards and Glory Girl flying a few feet above the ground.  They were swatting at the bugs crawling on them, but they weren't so distracted that they didn't notice the sudden emergence of light, or us.



``Glory Hole!'' Tattletale heckled the heroine, before opening fire on her.  Grue directed a stream at Clockblocker, to the left, so I turned my attention to the person on the far right of the group.  Shadow Stalker.



I admit, I had a reason to be ticked at her, since she wrote a note for Emma's dad, giving him fuel for that damned assault charge.  It was with a measure of satisfaction that I unloaded a stream of foam on her.



The stream was dead on, but she didn't seem to give much of a damn as she evaded to one side.  I caught her square in the chest with another spurt, making her stagger a bit, but she didn't fall or get caught in the stuff like the others.  Instead, she sort of ducked low, her cape billowing, and then rolled to one side, readying her crossbow as her feet touched the ground and she shifted to an all-out run.



Whether that was a tranquilizer shot or a real arrow, I was \emph{fucked} if she hit me.



I went wide with my stream, aiming to catch her a little and either slow her down or mess up her aim.  She stepped on a bit of foam and was tripped up a little.  Tattletale added her firepower to mine, and with our combined streams, Shadow Stalker fell.  We took a second to bury her under the foam, and Grue added a measure of darkness to it.



``Next!'' Grue hollered, pointing.  I hauled the heavy tank off the ground and moved closer to our next target before putting it down again and aiming.



This time, I deliberately moved a force of bugs into the area for some extra distraction.  The darkness dissipated, and it was the Protectorate this time, half of them.  Battery, Assault, and Triumph.



Battery was already charged up when Grue dismissed the impenetrable shadow that had covered them, and moved like a blur as soon as she could see where she was going.  She didn't bolt straight for us, though.  Instead, she leaped to one side, kicked Assault square in the middle of the chest with both feet, and then careened off in the opposite direction.



Assault was a kinetic energy manipulator, and could control the energies of movement, acceleration and motion much like other heroes could manipulate flame or electricity.  He used the energy from Battery's kick to rocket towards us, as Battery moved around to flank.



Grue directed a stream straight at Assault, but the first second of fire seemed to skim right off the man.  It did start taking hold after that, but the delayed effects gave Assault just enough time to slam into Grue and send him flying into the wall beside the Wards.  After that, the expansion of the foam kept him from moving much further.



Tattletale and I focused our fire on Battery.  The woman ducked and dodged out of the way of our streams, moving too fast to follow reliably with our eyes.  She seemed to stumble into a cocktail table, one of those round ones large enough for four people to stand around, but any clumsiness on her part was an illusion of the eye.  A heartbeat later, she had the table in her grip and was spinning in a full circle.



She threw the table like an oversize frisbee, and I pushed Tattletale in one direction as I flung myself in the other.  The table edge caught the weapon in Tattletale's hands and knocked it from her grip with enough force to make Tattletale roll as she hit the ground.



Which left only me standing, against Triumph and Battery.  Armsmaster, Miss Militia and Velocity were nowhere to be seen.  I could have used my bugs to feel out for them in the darkness, but I had more pressing matters to focus on.



Battery was charging again, taking advantage of us being off balance to build up a store of power again.  Heck, she'd probably built her whole fighting style around it.  I could see the normally cobalt blue lines of her costume glowing a brilliant electric blue-white.  I focused my attention on her, drawing every bug in the immediate area to her while I tried to get myself oriented to open fire again.  Wasps, mosquitos and beetles set on her, biting and stinging.



For just a fraction of a second, I saw the glow of the lines of her costume dim, before igniting again.  She needed to concentrate, it seemed, and my bugs had served to distract.  As I pulled myself upright and opened fire, she was a step too slow in getting out of the way of the stream.  I caught her under the spray and started piling it on top of her.



A shockwave blasted me.  I was knocked off my feet for the second time in a matter of seconds and my ears were left ringing.



Triumph had a gladiator/lion theme to his costume, with a gold lion helm, shoulderpads and belt, and skintight suit elsewhere.  He had managed to claw enough bugs away from his face to use his sonic shout.  He was one of those guys that was big, muscular and tough enough that you'd avoid him even if he didn't have that other power, and his other power was one that let him punch holes through concrete.



Grue aimed and fired a stream at him, but Triumph was surprisingly quick in slipping out of the way.  As Grue reoriented his aim, Triumph kicked over a cocktail table and grabbed it with one hand to use as a shield against the foam.  I tried to scramble to one side, to attack him from another direction, but he opened his mouth and unleashed another shockwave that sent me skidding across the floor, dangerously close to the piles of foam that had the Wards trapped.  As I tried to raise my nozzle in his direction to spray more containment foam at him, my vision swam and I saw double, and a high pitched whine threatened to drown out everything else.  I lowered the weapon, sent more bugs his way and focused on regaining my senses.



``Here!'' Grue hollered.  He raised his hand.  Triumph inhaled, gearing up for another blast-



And Brutus barreled through the corridor Grue had parted through in the darkness to slam into Triumph like a charging bull.



Maybe a little harder than I would have hit the guy, had I been the humvee sized monster making the call.  Still, you couldn't fault a dog for not knowing.



Just to my left, Shadow Stalker pulled her upper body free of the goop and began the slow process of working her crossbow free.  Not normally possible, but her ability to go into a shadow state apparently made her more slippery than most.



``No,'' I growled at her. ``Stay down.''  I buried her under more foam.



I pulled myself to my feet, wobbled, straightened up, wobbled some more, and then worked on keeping my balance.



``Skitter!'' Grue roared, ``Move!''



I didn't waste any time in throwing myself to the ground.  Out of the corner of my eye, I only saw a blur of blue and silver where I'd been standing.



I had to flop over onto my back to see Armsmaster standing six feet away from me, leveling the blade of his Halberd in my direction.  The silver of his visor made precious little of his expression visible.  All I could see was the thin, hard line of his mouth.



``Sorry,'' I mumbled, quiet enough that I was pretty sure Tattletale and Grue wouldn't catch it.  I aimed his way with the foam sprayer.



In a flash, he whipped his weapon around so the butt end was facing me.  There was a muffled `whump' sound, and I felt something like a wave of intensely hot air that made every hair on my arms, legs and the back of my neck stand on end.  I realized the trigger of the containment foam sprayer was depressed and nothing was coming out of the end of the weapon.  I tried again.  Nothing.



That would be an electromagnetic pulse screwing up the machinery.  Fuck.



Before I could organize my thoughts and warn Grue and Tattletale, Armsmaster flipped the weapon around in his hands like you saw military cadets doing with their guns during a march.  As it whirled around him, I heard that `whump' sound twice in quick succession.



Somehow, I doubted he'd missed them.



``Call off your mutant,'' he spoke, in that kind of voice that people \emph{obeyed}.  ``I promise you, it would only get hurt if it attacked me, and I'd rather not subject an animal to that, when it's the master that's to blame.''



``Bitch!'' Grue called, ``Call him off.  He's right.''



From a point I couldn't see, Bitch whistled.  Brutus moved back through the corridor Grue had made to rejoin her.



``You were moving like you could see in my darkness,'' Grue spoke, a note of wariness in his echoing voice.



``I've studied your powers,'' Armsmaster told us, tapping the butt of his weapon on the ground.  Every bug within fifteen feet of him dropped out of the sky, dead.  ``This was over from the moment you stepped into the room.''



Miss Militia stepped out of the darkness beside the stage, with what looked like a machine gun in her hands, Regent as her hostage.  He didn't have his scepter.



\emph{Fuck}.





