





``Surrender,'' Armsmaster ordered us.



``No,'' Grue retorted.



``You're only going to embarrass yourself if you prolong this.''



``We have you outnumbered five to three, eight to three if you count the dogs,'' Grue answered.  ``I can see your buddy Velocity lurking over there.''



``What do you hope to accomplish?  I admit, it was clever to control the battlefield, to dictate each engagement so it occurred on your terms, and to use our own weapons against us\ldots but those weapons no longer work.  \emph{None} of your weapons work,'' Armsmaster turned his head to look at where Miss Militia had Regent at gunpoint.  ``Which means you can stop trying to use your power on me, Regent.  I've got a little blinking light in the corner of my H.U.D. telling me you're trying something.  I've set up psychic and empathic shielding, to protect myself from you and Tattletale.''



I glanced at Tattletale.  He was psychically shielded against her?  How did that work?



Then I remembered.  When we'd gone up against Glory Girl and Panacea, hadn't Tattletale said she read minds?  And now Armsmaster had bad info and was figuring he was immune.



``I don't need to read you,'' she told him, ``You're the only one with shields, so your teammates and the PRT staff don't have any psychic shields up, and I can read them to get anything I need.  You're not the best inventor, but like most tinkers, you've got a knack.  Yours just happens to be condensing and integrating technology.  Only works in your immediate presence, but still, you can stick way more technology in a space than has a right to be there\ldots like your Halberd.''



Armsmaster frowned.  ``You're lying.''



Damn it.  I wish I could've told her he had a lie detector built into his helm.  But I couldn't without explaining that I knew him.



Tattletale took it in stride, grinning, ``Sure, fibbed about the reading minds bit.  Not about your weapon and power.  Let's see\ldots to deal with my buddy Grue, you've made that thing a fancy tuning stick.  Sensing vibrations in the air, translating them into images with that fancy helm of yours?''



Grue cracked his knuckles.  He'd gotten the message.  Darkness wasn't going to do much.  Armsmaster, for his part, gripped his weapon tighter.  An unspoken threat to Tattletale.



``And the ass-end of that stick of yours is using the brass in between the floor tiles to help transmit an electrical charge to the area around you for fancy bug zapping.  Did you set that up before coming here tonight, knowing the way the floor would be put together?''



He didn't reply.



``Guess not.  Happy coincidence that the setup you put together works as well as it does in here, then.''



Again, no reply.  She grinned a fraction wider.  She went on, ``You can tell I'm lying, huh?  That's awesome.''



Armsmaster's weapon turned to point in her general direction.  She didn't back down.



``So you'll know I'm telling the truth when I say your team \emph{hate your guts}.  They know you care more about rising from your position as the seventh most prominent member of the Protectorate than you do about them or the city.''



In the span of a second, the blade of the halberd broke into three pieces, reconfigured, and fired in grappling-hook style at Tattletale.  The tines closed together, forming a loose ball shape as it flew, striking her solidly in the stomach.  She crumpled to the ground, arms around her middle.



The head of the weapon reeled in and snapped back into place atop the pole.



``Bastard,'' Grue spoke.



``Apparently, according to your teammate,'' Armsmaster replied, seemingly unbothered.



I gathered my bugs, poising them near and above Armsmaster in case I needed them to act quickly.



Armsmaster turned his head in my direction, ``Skitter?  You, especially, do not want to irritate me any more, tonight.''



The bottom of his Halberd tapped the ground, and the bugs perished.  I glanced at the floor as he did it.  Sure enough, the broad tiles had little lines of metal -bronze?- dividing them.



There was a flurry of action where Regent and Miss Militia were.  She appeared to drop the machine gun, and Regent took that chance to pull away.  He didn't get one step before she regained her balance and dropped into a low kick that swept his legs out from under him.  Her machine gun dissolved when it was halfway to the ground, turning into a shimmer of dark green energy that arced back up to her hand.  It rematerialized into a gleaming steel machete.  Regent stopped his struggles the second she rested the point of the bladed weapon against the side of his throat.



Armsmaster watched it all unfold without twitching a muscle.  Even if he didn't care much about his teammates, he apparently trusted Miss Militia to handle herself.



``Grue.  You've shown you can dismiss the effects of your power,'' Armsmaster spoke, ``Do so now.''



``Somehow,'' Grue retorted, ``I'm not seeing a major reason why I should listen.''



``Um, got a sword pressing against my neck here, guy,'' Regent pointed out.



``\ldots{}Not seeing a major reason,'' Grue repeated himself.



Regent let out a little laugh, ``Fuck you.''



Armsmaster dispassionately watched the exchange, then spoke, dead serious, ``Look at it this way.  If there are witnesses, Miss Militia will have a far harder time selling the idea that she stabbed your friend in the throat in self defense.''



He glanced in the direction of his second in command, and Miss Militia gave a small nod in response.



Would she?  Probably not, I suspected.  Could we risk it?  That choice was up to Grue.



Grue glanced over at where Regent lay.  After a second, he made the darkness fade.  The people in the crowd were mostly huddled on the ground, trying to fend off the stinging and biting swarm.  The dogs lurked at the edges of the room, and Bitch was astride Angelica.  Velocity, in his red costume with the racing stripes down either side and two stripes meeting in a `v' at his chest, wasn't that far from her.  I suspected they had been squaring off.



I found Emma in the crowd.  Her dad was huddled over both of his daughters, as though he could shield them from any danger, and Emma's mom was hugging her around the shoulders.



Somehow, that \emph{really} pissed me off.



Armsmaster glanced my way, ``And the bugs.''



Reluctantly, I pulled them away from the crowd.  I settled the flying bugs on the intact portions of the ceiling.  I glanced up at the bugs and sighed.  Then I glanced at Emma again.



This was \emph{really }not how I wanted this to end.  Me arrested, my scheme a failure, Emma getting off scott free with a family, friends and no major consequences for all the shit she'd pulled?



``Sir,'' I spoke, trying to sound confident.  \emph{Would Emma recognize my voice?}  ``Let me check on Tattletale.''



``You can do that once you've surrendered,'' he spoke.  He changed his posture so his Halberd was pointed in my general direction.  I winced.  I did not want to get the same treatment Tattletale had received.  Or would he not do it with people watching?



My eyes darted in the direction of the crowd, to Tattletale, who didn't look up to talking.  All eyes were on the scene.  Why had he gone out of his way to get an audience?  Could I use it?  What had he been so upset about, when I'd met him at the ferry?  What had Tattletale gone out of her way to stress to us about Armsmaster?



Reputation.



``I need to make sure you didn't do any serious damage,'' I spoke, just a hint of accusation in my voice.



``She's fine.''



``I want to verify that for myself,'' I said, standing.  \emph{How far can I push this?}  ``Please, she was surrendering and you hit her so hard.''



``You're lying.''



``The fuck she is!'' Regent joined in, ``Tattletale walks up to you, ready to be cuffed, and you smacked her across the room, you \emph{fucking lunatic}!''



I didn't dare to glance at the crowd.  Armsmaster was the person we needed to get a reaction out of, here.



``Enough.  This is a fabrication,'' Miss Militia spoke, her voice raised maybe a bit to carry to the rest of the room.



``Why do you think we're so reluctant to surrender, if that's the treatment we'll get!?'' Regent shouted, ``It's not like we're not totally fucked!''  Miss Militia moved the machete to remind him it was there.



Armsmaster's head turned toward me.  This was my huge gamble.  How would he respond?  If he called me out as a traitor within the Undersiders, would people buy it, would my \emph{team} buy it, or would it only hurt his credibility?  He didn't know that Tattletale would be able to tell it was truth.



``Miss Militia has a blade at my teammate's throat,'' Grue broke the silence, ``I think it's pretty clear you don't pull your punches.''



Armsmaster turned to his teammate, ``Perhaps a less lethal weapon would be more appropriate.''



Miss Militia's eyebrows knit together in concern, ``Sir?''



``Now.''  He left no room for argument.  Then, to ensure they still had control of the situation, he turned to his nearest available hostage.



Me.



I was flat on my back and couldn't back away fast enough to escape, especially with my having to slip my arms from the straps that held the tank of containment foam to my back.  He pointed the head of his weapon at me as he strode over to me, the threat of his firing it serving to keep me subdued.  I glanced at Grue, but he was frozen, two of his teammates at the mercy of the city's leading heroes.  Tattletale was struggling to her feet, but she couldn't accomplish much.



Above Regent, the sword shimmered and turned into that black and green energy.  In that moment, Regent struck, drawing his knees to his chest, then kicking up and to the side to drive both of his heels into Miss Militia's upper stomach.  A second later, he shoved both of his hands in the direction of her collarbone.



The black-green energy of her power continued to arc around her without solidifying as the contents of her stomach began violently heaving their way out of her mouth, spattering into the flag-scarf that covered the lower half of her face and overflowing onto the floor.  Regent had to roll to one side to avoid being bathed in vomit.



I took advantage of the distraction and brought every bug in the room down from the ceiling, sending a fair majority of them toward Armsmaster.  He swiped at his face to remove them, then lifted his weapon.  I grabbed for the pole with both hands before it could strike the ground, and pulled myself across the floor to situate my body between the pole and the ground.



It didn't feel like I thought it might, the electrical charge.  As the end of the Halberd made contact with my body, it was as though someone had dropped a handful of live snakes onto my chest and they were writhing in place there, a single tendril rushing up the skin of my right arm and over my fingertips.  It didn't hurt much at all.



And the bugs around Armsmaster didn't die.  Very few of the ones on me, even, perished.



I'd known spider silk was insulated to some degree.  I was really glad that it was insulated \emph{enough}.  Really, really glad my interference was enough to stop the energy from conducting through the area and zapping the bugs out of the air.



``Hm,'' looming over me, Armsmaster made a noise of disapproval, ``Not smart.''



``Bitch!  Dogs!'' I hollered, ``Grue!  Shadow me!''



Of all the times to lapse into caveman grammar.  Still, he smothered me and Armsmaster in darkness.



When Armsmaster managed to wrest the Halberd from my hands, I had enough bugs on him to tell he was bringing the bottom end of his Halberd down hard against the floor, away from me.  My bugs didn't die, and continued to settle on the exposed skin of his lower face, crawl up under his visor.  The charge or whatever other stuff he had going on to direct it wasn't conducting through the darkness.



Before he could strike at me, I headed in the other direction.  Staying in close proximity to Armsmaster wasn't a good idea, with my power being one that worked at range, and him being the close-quarters combatant.  I felt him move away from me, clawing the bugs away from his mouth and nose, heading out the opposite side of the cloud of darkness to strike the ground, kill off the swarm I'd set on him and then turn his attention to the charging dogs.



I wasn't two steps outside of the darkness when I had Velocity in my face.



Battery and Velocity were both speedsters of a sort, giving them the ability to move at a ridiculous pace.  They were very different \emph{kinds} of speedster, though.  As I interpreted it, from all the stuff I'd read online and in the magazines and interviews, Battery could charge up and move at enhanced speeds for very short periods of time, sort of like how Bitch's power pumped up her dogs, but concentrated into a few brief moments.  It was a physiological change, altering her biology and then altering it back before it became too much on her body.  The actual act of moving at the speeds these guys could manage was an incredible strain on the body.  There were only one or two parahumans on the planet who could manage that kind of movement without any workarounds or limitations, and Battery and Velocity weren't among them.



Velocity, in contrast to Battery, was more like Shadow Stalker.  He changed \emph{states}, and while I had no idea what this meant exactly, whether it was him shifting partially into another dimension or altering the way time or physics worked in relation to himself, I did know that it made him able to move very fast, without needing to rest like Battery did.  Fast enough that my wasps couldn't really land on him, and those that did were dispatched before they could start stinging.



The drawback, though, was that while he was moving like that, he wasn't hitting as hard, probably for the same reasons he wasn't shattering his bones by hammering his feet against the ground ten times a second, getting torn to shreds by friction or running out of oxygen due to an inability to breathe.  His speed came with a reduced ability to affect the world around him and be affected by it.  He couldn't hit as hard, couldn't hold or move things as easily.  An effective loss of strength proportionate to how fast he was capable of moving.



So as fast as he was moving, having him hit me wasn't much worse than getting punched by an eight year old.



Problem was, he was hitting me a \emph{lot}.  His perceptions were ramped up, too, which meant he had the luxury of what must have been \emph{seconds} in his own senses to see my reactions, calculate the best place to stick that next punch or kick to knock me off balance or inflict pain.  It was less like being in a fistfight and more like being caught in a gale-force wind that had every intent of screwing me over.



Velocity was forcing me to back up, stumble and overall just working to herd me in one direction – towards an open window.  Either he'd force me through and leave me hanging from the ledge, helpless to avoid arrest, or I'd have to give up or let myself be knocked to the ground instead, at which point it would be pretty much over.  Once I was down, he'd either keep up the onslaught until another cape could finish me off, or he'd turn off his power long enough to knock me over the head a few times with a chair or something.



Across the room, Grue was working with two of the dogs and Bitch to keep Armsmaster hemmed in, while one of the dogs and Regent were keeping Miss Militia out of action.



I couldn't win this one on my own.



``Grue!'' I hollered.  I got struck in the mouth three times before I could bring an arm up to fend Velocity off and speak again, ``Need cover!''



He spared me a glance and a blast of his darkness.  In an instant, I was blind and deaf, with only my bugs to go by.



But Velocity was slowed down, and I had my suspicions that it wasn't just the fact that he had to use his hands to find me before striking.  Grue had said that Shadow Stalker's powers were somehow less effective in his darkness.  Could that apply to Velocity too?  Or was it just the extra resistance of Grue's power versus normal air, combined with Velocity's low strength?



My bugs were now successfully settling on him, oddly giving me a better sense of his movements than my eyes had, and I was directing them not to sting or bite, so he wouldn't have an easy time finding them.  They began to cluster on him, and somehow I felt like that was slowing him down even more.



The onslaught had been softened, and he wasn't half as effective at keeping me off balance, now.  He couldn't effectively see my posture to know the optimal places to strike, so I was able to get my feet firmly on the ground.  I lashed out twice with my fists, but my hits lacked impact.  Something to do with his power, I suspected, as well as his ability to move fast enough to roll with any hits he felt connecting.



So I grabbed a weapon he couldn't react to, my pepper spray, and directed a stream of it into his face.  \emph{Then} I instructed the bugs I'd gathered on him to bite and sting.



The effect was immediate, and dramatic.  You've never really seen someone flip out until you've seen a speedster flip out.  He fell to the ground, stood, tumbled over a chair, then was up the next second, lunging for a table, blindly patting it down in the hopes of finding something to wash his eyes out with.  I felt him slow down dramatically, increasing his own strength enough to allow himself to check the cups and pitchers.



I had bugs on the table he was searching, and the only liquid there was wine.  Anticipating he would continue looking for some relief, I moved closer to the table nearest me.



Sure enough, he darted over to the same table and began searching.  I took one long step to my left, reached behind my back, and gripped the foam handle of my extendable baton with both hands.  Like a golf club, I swung it up and between his legs.



My rationale was that I needed to hamper his mobility, but I didn't want to deliver any permanent injury, which was a possibility if I hit him in the knee or spine.  Besides, the Protectorate had top notch costume designers, and what male superhero with an expensive costume would go out without a cup?  Right?



Unless, the thought crossed my mind as Velocity keeled over, he'd foregone the cup for extra mobility and to reduce friction.



I'd find some way to make it up to him, after all of this was over with.



He pulled weakly against my grip as I brought his left arm and his right leg together, and cinched them together with a double-set of plastic handcuffs.  I then cuffed his right arm to the table in front of him.  Velocity was out of action, for all intents and purposes.



Though every impulse told me to get out of the darkness and get a look at what was going on, I stayed put, crouching and feeling out with my bugs.  With their legs and bodies serving as thousands upon thousands of tiny fingers I could use to feel out my surroundings, I got a sense of the situation.



Since doing whatever he'd done to Miss Militia, Regent had taken to standing guard over her.  He had one hand outstretched in her direction while she struggled on the floor, dry heaving now, with her limbs twitching.  Tattletale was with him, one hand still pressed to her stomach, but she was standing, watching the crowd for anyone who might step to Miss Militia's rescue.



Which left only Armsmaster.  Except `only' wasn't the right word.  Bitch, her three dogs and Grue had Armsmaster surrounded, and even with that, I got the impression that he was in control of the situation.



He'd formed the head of his halberd into a loose ball again, and had the chain he used for the grappling hook extended partially so it could serve as a flail.  There was something of a stalemate as my teammates remained where they were, staying spaced out, just out of reach of the weapon.  Armsmaster, for his part, was standing in a loose fighting posture, holding the long pole of his Halberd as he swung the flail head in a loose figure eight.



Brutus growled at his quarry, moving a half step too close, and Armsmaster seized the opportunity.  The chain extended with a faint whirr and the flail moved with surprising quickness to collide with Brutus' shoulder.  From Brutus' reaction, I would have thought he'd just been hit by a wrecking ball.  Either Armsmaster was far stronger than he looked, or there was something about his weapon that was giving it a little extra oomph.  Given that he was a tinker, it could have been \emph{anything}.



Armsmaster didn't stop at felling Brutus.  As he finished giving the ball the necessary momentum, Armsmaster reversed his grip and lunged at Grue, swinging the bottom end of his weapon like a baseball bat.  Grue avoided the swing by stepping back and ducking, but wasn't able to recover quick enough to avoid the follow-up.  Armsmaster kept moving forward, not pausing as he slapped the end of the pole back into one of his hands and rammed the midsection of the pole against Grue's chest, hard.  Grue hit the ground with enough force that he almost bounced, and was driven hard into the ground a second time as Armsmaster brought the end of the pole down into his stomach.



Without thinking, I stepped forward out of the darkness, then stopped myself.  What help could I offer by jumping in there?



Bitch whistled for a dog to attack, but Armsmaster was already reacting, drawing his elbow against the chain to control the movement of the flail's head.  He dropped the pole and grabbed the chain to pull the ball towards himself, caught it out of the air with his free hand and turning in a tight circle to preserve the momentum from flail-head's flight, slammed it full force into Angelica's ear.  Bitch had to skip back out of the way as Angelica collapsed to the ground where she'd been standing.



Without glancing down, Armsmaster put one armored boot underneath the pole as it rebounded against the ground, then kicked it straight up to chest level.  He caught his weapon in one hand and reeled in the chain.  The flail-head snapped back into a blade shape as it reconnected with the top of the pole.



Two dogs and Grue down, and he'd made it look effortless.



It struck me just what made Armsmaster a step above other tinkers, above other people with the ability to invent and perform mad science, and it wasn't the insane amounts of training he had probably put himself through.  Tinkers tended to have a knack, a special quality specific to their work.  According to Tattletale, Armsmaster's ability let him cram technology together and still have it work.  Other tinkers were limited in what they could carry and have access to at any given point in time, but Armsmaster?  He had a solution for every problem he'd been able to think of, without having to worry about economy of space, the weight of his hardware and the room on his utility belt, or whatever.  And with all of that, his main gear, his armor and Halberd, were still devastating and completely reliable in their own right.



While Armsmaster had his back turned to her, I saw Tattletale step to one side, surreptitiously.



Judas lunged, and in the same moment Armsmaster reacted, Tattletale made a move for the crowd, drawing her gun.



I glanced towards Armsmaster, and my view of him was blocked as Judas collapsed to the ground between us.  Through my bugs, I sensed him extend his weapon towards Tattletale, felt the recoil as the head of it rocketed off.  The grappling hook caught her gun hand with enough force to screw up her aim, and the tines of the hook closed around her arm.



He reeled in the chain at the same time he pulled it back toward him, and in doing so, flung Tattletale across the floor.  The tines let her go just in time to send her careening into one of the flimsy cocktail tables.  Armsmaster jerked the pole of his weapon to control the flight of the hook as it reeled back in, striking Tattletale's gun out of the air and shattering it into pieces.



``No hostages,'' he said, ``No guns.''



Grue started to stand, fell, then managed to stand successfully on his second try.  The three dogs Armsmaster had dropped were taking longer to get upright.  Angelica shook her head violently, twice, paused, then did it again.



Armsmaster looked at Bitch, then slapped the pole of his weapon against the palm of his armored glove.



``Rachel Lindt, AKA: Hellhound.''



``Armsmaster, AKA: dickhole,'' Bitch retorted.



``If this goes any further, I can't promise those animals of yours won't suffer permanent damage.''



I could see her eyes move behind the eyeholes of her mask as she cast a sidelong glance to her left to look at Brutus, then to her right, at Angelica.  Then she met his gaze, ``You do lasting damage to any of them, we'll find you and do ten times worse to you.  Trust me, old man, they know your smell, we can track you down.''



Again, the pole slapping against his glove with a sound of metal against metal.



His tone was measured as he asked her, ``Why risk it?  You've already lost.  We had enough footage of your dogs that I was able to put together a simulation of their fighting patterns.  I know how they attack, how they react.  I know how \emph{you} think in a fight, the commands you give, and when.  All of that is wired into my suit, into my heads up display.  I know what you and your beasts are going to do before you've decided on it.  None of you are walking away.''



``It's not just me and the dogs,'' Bitch spoke.



``Your friends?  I may not have a simulation set up for him, but I'm \emph{better} than your leader, Grue.  Stronger, better armored, better equipped, better trained.  If your friend Regent turns his attention from Miss Militia for more than twenty seconds, she will shoot one or all of you, not that he could do anything to me if he bothered.  Tattletale?  Unconscious.  Skitter?  Not a threat.''



What was he doing?  Why was he so focused on getting Bitch to admit it was over?



Reputation, yet again.  He needed to salvage this situation, and the surest way to do that, to recoup his losses and come out of this looking okay, would be to get the meanest, toughest, most notorious of us to bend at the knee and concede defeat.



He really didn't know Bitch, though.



She pulled her cheap plastic dog mask off and threw it to one side.  It was only a formality, really, since her face and identity were public knowledge.  Her smile, as it spread across her face, wasn't the most attractive.  Too many teeth showing.



``Lung underestimated her, too,'' she told him, looking at me.



Armsmaster turned to look, as well.



\emph{Seriously}?  I mean, \emph{really}, Bitch?  Passing the ball to me?  I didn't have a plan.  There wasn't much I could do, here.



``Velocity?''  Armsmaster queried me, casual.



I shrugged, miming his casual tone, while feeling anything but, ``Dealt with.''



``Hm.  I think-''



As he spoke, I faced Grue and jerked my head in Armsmaster's direction.  Armsmaster wasn't oblivious, and took my cue as reason to drop into a fighting posture.  There was nothing he could really defend against, though, as Grue shrouded the two of us in darkness a second time.



The worst possibility, that Armsmaster would tell the Undersiders what I was planning, was dealt with for the moment.  I doubted Armsmaster would continue to talk while under the effects of Grue's power.



Which left me the problem of dealing with the guy.  I could sense the bugs I had on him moving, as he came through the darkness, towards me.  At the very least, if I could draw him away from the others, I could buy them time.



I ran for the glass door that led to one of the outside patios.  I glanced over my shoulder, and sure enough, I saw Armsmaster emerging from the cloud of oily shadow.  He spun on his heels to swing his flail into Judas, bringing the dog down as it emerged right after him, then whirled to face me again.  As I got outside, the chain reeled in, bringing the flail head back to the top of the weapon.  He paused.



Why?  There was only one reason he'd be staying back and reeling in like that, instead of closing the distance to get me in his reach.



I took a guess.  Knowing that the attack would come faster than I expected, from what had happened to Tattletale on the two occasions, I threw myself to the floor of the patio.



The ball came flying out of the end of his weapon, but my attempt to dodge did little good.  He whipped the chain to shift the sphere's trajectory, and simultaneously opened it into its oversized grappling hook form.  The thing hit me in my side, with the tines passing over each of my shoulders and under my armpits.  I grunted with the impact, and as I tried to stand, I nearly slipped on the excess chain that spooled around me in the grappling hook's wake.  I felt the claw of the hook tighten around my chest.



On the far side of the patio, Armsmaster planted his feet and raised his weapon to start reeling me in.



\emph{No, no, no, no, no.}



I was \emph{not} going down like this.



\emph{Not with Emma fucking Barnes and her asshole lawyer dad in the crowd.}



I started to gather my bugs from inside, but stopped.  No use bringing them here, when Armsmaster could murder half the swarm with that souped up bug zapper he'd worked into his Halberd.  I moved my bugs into position indoors.



Still shaky from the hit, thankful for the armor I'd built into my costume, I managed to grab the excess chain below me and wind it around the patio's railing behind me.  If Armsmaster wanted me, he'd have to come to me, dammit.  I wasn't going to make this easy.



The chain grew taut, and Armsmaster tugged twice before deciding it would be less trouble to approach than to add to the property damage.  He closed the distance to me on foot, pausing only to free his chain from the patio railing.  He reeled in his chain to pull me the remaining two or three feet to him.



``Skitter.  I would have thought you would be quicker to surrender.''



Nobody else was in earshot.  ``Whatever side I'm on, I don't exactly want to go to jail.  Look, my offer stands.  I've almost got the last bit of detail I need from these guys.''



``Something you said you'd have weeks ago,'' he replied.



``There's no other way you're going to salvage this, Armsmaster,'' I stood as straight as I could with the grappling hook around me.  The damned thing was heavy.  Tattletale had gone out of her way, even got herself knocked out of action, to let us know how important Armsmaster's status was to him.  I needed to use that.  ``Only way you won't look incompetent is if you can say I only got away because \emph{you let me}.  That all of this tonight happened \emph{because you let it}.  Because letting me get away with this meant I could get the info on who's employing the Undersiders, on where the funding, equipment and information is coming from.  Then you clean up, and it's two supervillain groups dealt with in the span of a week.  Tell me that doesn't sound good.''



Armsmaster considered for a moment.



``No,'' he answered me.



``No?''



``Don't expect anything other than a prompt arrest for you and your companions for your antics tonight,'' he shook his head, ``A bird in the hand, after all\ldots''



He gave me a little shake, as if to make it clear just who the bird was.



I took a deep breath, ``You were right, Armsmaster.''



``Of course,'' he spoke, absently, pushing me against the railing with one hand.  His grappling hook released me, reconfiguring into what I suspected was the same setup that had fixed Lung to the ground with bars of stainless steel, back in my first day in costume.  It was shaped like a rectangle, and there were two `u' shaped bands of metal with electricity arcing around them, the tips of each `u' glowing hot enough to melt against any surface.



``This was over from the moment we stepped into the room,'' I finished.



Nearly seven hundred hornets exploded from underneath my panels of armor, all latching onto him, biting and stinging relentlessly, flowing underneath his visor, into his helmet, his nose, mouth and ears.  Some even crawled down beneath his collar, to his shoulders and chest.



I threw myself at the tail end of his Halberd, hugging my body around it.  With one hand he lifted me and the Halberd both, and slammed us against the ground.  Again, I felt those tendrils of electricity running over me, on top of the pain of having my stomach caught between the pole and the ground.  I was very thankful, the second time tonight, for the panels of armor I'd implemented into my costume design.



He repeated the process, lifting me two or three feet off the ground, then slamming the pole and me down again.  After the second time, I had to fight to place myself beneath the pole again in anticipation of a third hit, knowing he would weather the onslaught of hornets longer than I did this abuse.



Rescue couldn't have come a second later.



Bitch, an unconscious Tattletale and Brutus were the first ones over the edge of the patio.  Brutus bumped against Armsmaster as he passed, knocking the man off balance and giving me the chance I needed to heave myself upright and pull the Halberd from his grasp.  I held it in my hands, and he was too distracted by the swarming hornets to even realize it.



I threw the Halberd over the edge of the patio and ran toward the door leading back inside.  I caught Grue's reaching hand as he and Judas bounded through, so he could swing me up behind him.



As we leaped from the patio's edge, I looked behind us and saw Angelica and Regent following.  Grue was banishing his darkness, to make the mess we'd created all the more clear for those of our audience that hadn't yet managed to flee.  Our objective was to humiliate, after all.



For much the same reason, maybe as a bit of a spiteful `fuck you' to Armsmaster, who'd made this all so much harder than it had to be, I left my bugs where they were, arranged on the wall to the right of the patio and the floor in front of it.  Half were gathered into the shape of two large arrows pointing to the patio door, one on the floor and one on the wall, while the other half were arranged into bold letters spelling out `LETS GO'.



I wrapped my arms around Grue, holding him tight as much in anticipation of our landing on a nearby rooftop as a farewell hug.



Chances were good that this was my last job as part of the Undersiders.





