





Leaping from rooftop to rooftop was not as awesome or efficient as it was on TV and in the movies.  Even if it was the dogs doing the brunt of the work, they weren't the most graceful of creatures, they weren't built to be ridden, and we didn't have any saddles.  There was also the distinct issue of there being buildings of wildly varying heights, similar to how Brian's neighborhood sported old Victorian style buildings amid apartments and condos.  As Judas hopped down from the side of a six story building, dug his claws into the side of a neighboring building to slow his descent, then jumped the rest of the way down to the asphalt of an alleyway, I was genuinely concerned the landings would dislocate my hip.



In short, I was grateful to be back on terra firma.



``Need a hand!'' Bitch called out, a moment after Brutus set down.  She had a prone Tattletale lying across her lap and Brutus' shoulders, and it looked like Tattletale was falling off, despite Bitch's best efforts to hold on to her.



I reluctantly let go of Grue as he slipped down from Judas and rushed over to help.  I silently lamented having included the panels of armor on my chest and stomach, which had been a solid barrier between my body and his back as I clung to him on our retreat from the Forsberg Gallery.



Whatever my regrets, I wasn't oblivious to the matter at hand.  I hopped down off Judas' back and hurried over to help with Tattletale, just a step behind Grue.  It proved easier to slide her down to the sidewalk than to get her back up onto Brutus' back.  Grue did the heavy lifting, while I focused on keeping her head and arms from hitting the ground or getting caught under her.  As I bent down to help ease her to the ground, I could already feel the stiffness in the muscles of my thighs, back and stomach.  I was glad I'd done my morning exercise earlier, because there was no way I was going to be able to go anywhere tomorrow.



I glanced around us.  Cars were zipping past on the streets at either end, but there weren't many pedestrians, and none appeared to have spotted us, thus far.  My suspicions were that most people in the downtown area who were out and about would be near Lord Street, celebrating the end of the curfew.  People would be acting out their relief over the end of the ABB situation, making up for time they'd spent cooped up in their homes during the six nights of curfew.



``Anyone see capes following?'' Grue asked.



``I didn't see anyone, but I wasn't really looking.  That's usually Tattletale's job,'' Regent replied.



``She can't give us any info like this,'' Grue pointed out.



``Wait,'' I told him.  I reached back into my utility compartment and fished out the changepurse.  I removed the tissues I'd wadded up inside to keep the change from rattling and found one of the three tiny white packets at the bottom of the bag.  I tore the packet open and held it under Tattletale's nose.



``Smelling salts?'' Grue asked.



I nodded.  ``You asked if anyone had any after we put down \"{U}ber and Leet.  I made a mental note to have 'em for next time.''



``I bet half of us did,'' Regent replied, ``The weird thing is that you actually followed through, dork.''



``What's weird about that?'' I asked, a bit defensively.



He was distracted from replying.  Tattletale stirred, turning her head to get her nose away from the smelling salts.  I moved them back under her nose.



She woke, mumbling, ``Okay, stop.''



``Welcome back,'' Grue told her.



``How do you feel?'' I asked.



``My stomach feels like someone ran it through a blender, and my arm hurts like hell, but I'm tougher than I look,'' she said.  Not one second later, she groaned and huffed out a breath, ``But I'm going to need help to stand.''



Grue and I helped her.  She was hurting, and moved at a glacial pace.  It was made more difficult by the fact that she apparently didn't want either of us to touch her right arm.



``What'd I miss?'' she asked, as if to distract from the fact that she was moving like an old woman.



``Tee el dee arr, you got bitchslapped and knocked out, it was down to Bitch and Skitter, and we still got away,'' Regent shrugged.



Tattletale froze in her tracks.  Since Grue and I were still easing her to a standing position, I was forced to shift my grip to ensure she didn't fall.



``\emph{Shit},'' she managed to fit more invective into that one word than some of the people from my dad's work could manage in ten, and some of those guys were seamen. Tattletale turned her head, ``That's not-''



``Not true,'' Armsmaster spoke, echoing her words as he rounded the end of the alley.



He looked worse for wear.  The lower half of his face had welts on it, not many, but some.  I'd instructed the hornets to sting so they weren't coiling their abdomens, which meant they weren't squeezing the venom sacs and injecting venom with every sting.  I'd only injected enough venom to make it hurt a little, to distract.  After I'd beaten my retreat, though, I knew some would have stayed on him, and a few would have stung him after I was out of range and no longer able to control the hornets.  The welts weren't the bad part, though.  What caught my eye, though, were the six thin trickles of blood running down the lower half of his face.  Hornet bites weren't necessarily capable of penetrating skin, as much as they might hurt, but there had been a lot of them, and if a few happened to bite in the same location, or if they caught the edge of an eyelid or nostril?  Maybe.  I noticed his Halberd in his right hand.



When I looked at our remaining escape route, Dauntless was at the other end of the alley.  Brockton Bay's rising star.  It would have been easy to peg him as a tinker, but he apparently wasn't.  His power let him, according to details he'd leaked when he'd appeared on TV and in magazines, imbue his gear with a little bit of power every day.  Thing was, every bit of power he parceled out had permanent effects.  Every day, he was just a little bit stronger than he'd been the day before.  A little bit more versatile.  It was expected that he would eventually surpass even the likes of Alexandria, Legend and Eidolon, the `triumvirate' of the Protectorate, the top dogs.  That kind of made him a big deal in Brockton Bay, a hometown hero.



I didn't follow that stuff, didn't buy into the hero worship.  I'd always found the capes \emph{interesting}, I'd followed the non-gossipy news about them, but with the exception of a phase around the time I was nine where I'd had an Alexandria t-shirt and had my mom help me find pictures of her online, I had never really got giddy over any particular hero.



Dauntless packed a few trademark pieces of gear.  He had his Arclance, a spear he held in one hand that looked like it was made of white lightning.  His shield, fixed to his left forearm, was a metal disc about the size of a dinner plate, surrounded by rings of the same kind of energy that made up the spear.  Finishing his current set of empowered items were his boots.  His feet looked like they were encased in the white crackling energy.  If rumor was to be believed, he was working on empowering his armor as well, but I couldn't see any hints of that energy on the costume.  It was white and gold, and his golden helmet was in the Greek or Spartan style, with slits for the eyes, a band of metal covering his nose, and a slit running down lower half of his face.  A band of metal crested the top, like a mohawk.



You could see the frown crease Armsmaster's damaged face as he turned his focus to me.



``I threw your Halberd off the side of the Gallery,'' I spoke before he could.  ``Did Dauntless fetch it for you?''



He didn't voice a reply right away.  As if to demonstrate, he threw his Halberd straight up in the air.  It disappeared into a storm of glowing blue lines as it reached the peak of its ascent, simultaneously rematerializing in his hand.  Hadn't I seen Kid Win bring his cannon to the site of the bank robbery in the same way?  A piece of borrowed technology?



``I'm not about to put so many eggs in one basket without sufficient safeguards,'' Armsmaster told me.  His voice was tight with repressed anger.



No bugs.  Damn it, I had no bugs, again.  I'd emptied my armor of bugs when I attacked Armsmaster, and I'd left them and the rest of the swarm back at the Gallery when I made my retreat.



``\emph{Surrender},'' he intoned.



``Thinking about it,'' Tattletale spoke.



``Decide fast,'' Armsmaster growled.



``Why did you guys stop here?'' Tattletale murmured to us, ``We're, like, half a block from the parking garage where we stashed our ride.''



``I wanted to make sure there were no pursuers before we peeled out,'' Grue replied, ``Good thing, too.''



``Right,'' Regent's voice was thick with sarcasm, ``Because this is \emph{so} much better than them finding us as we put the key in the ignition.''



``Guys,'' I cut in, whispering without taking my eyes from Armsmaster, ``Answers.  Solutions.''



``Get to the parking garage,'' Tattletale told us.



``Our situation there won't be any better,'' Grue countered.



``\emph{Get to the parking garage},'' She hissed through her teeth, as Armsmaster took a step forward.



The alley was wide enough for two dogs to stand shoulder to shoulder, and I saw Bitch directing two of the animals to stand between us and Armsmaster before Grue blanketed everything but Armsmaster and the dogs in darkness.



The darkness didn't last more than three seconds.  There was enough time for Grue to place his arm against my collarbone and shove me back against the wall, and then he removed the darkness around us.  There was a smell like burning ozone.  Had Dauntless used his spear?



It was immediately clear that Dauntless didn't have much darkness around him.  He was holding his shield arm up, and it had formed into a bubble-shaped forcefield, extending in a ten foot radius around himself, touching both walls on either side of us.  The forcefield was serving to block off the darkness, and while I wasn't sure, I suspected that the field was actually eating through any darkness that touched it.  It was making a continual sizzling, crackling sound that drowned out the traffic on the roads around us.



Dauntless advanced a pace, and the forcefield moved a corresponding distance closer to us.



After a second short advance from Dauntless, Grue had to back up a step to avoid touching the field of crackling white energy.  A step that closed the distance between us and Armsmaster.



``Armsmaster hates you,'' Tattletale told Dauntless, raising her voice to be heard over the crackling sound the forcefield was generating, ``He hates that you're the next big thing, the guy that's going to be better than him.  That you get the easy road to being a big name in the Protectorate, and he's the one that has to stay up nights, reworking his stuff, compiling simulations, coming up with new ideas, training in the gym for hours and hours on end.  Every second of work he puts in, he gets more and more resentful of you.  Why do you think you were the \emph{one} member of the team he sent off to patrol the city and watch over the Wards, instead of having you come to the party?''



Dauntless shook his head.  Then he raised his spear hand and tapped one finger against the side of his helmet.



``Ear buds,'' Tattletale sighed, ``Armsmaster told him to wear ear buds, so Dauntless can't hear anyone but him.  That's both brilliant and incredibly depressing.''



Dauntless advanced two steps, quickly, and all of us, excepting Bitch and Angelica, were in a position where we had to hurry to step back.  Regent was too slow, and his hand touched the bubble.  A brief arc of energy traced from the field to Regent's hand as he pulled it back.



``Fuck!  Ow!''  Regent gasped.  ``Enough of this shit!''



He raised his other hand, and Dauntless stumbled.  Regent then brushed his hand to one side, and Dauntless fell.  As Dauntless used both hands to ease his fall, the forcefield dropped away.



``Go!'' Grue bellowed, dismissing his darkness.  Bitch whistled twice, hard, and the two dogs that were fighting Armsmaster hurried to follow.



Dauntless raised his spear to impede us.  Grue, leading our retreat, leaped over the crackling beam of lightning and brought both feet down on Dauntless' helmet as he landed.  The hero didn't recover before we were over and past him.



We were free of the alley.  Two of the dogs surged past us, getting in the way of incoming traffic so we were clear to cross the street.  Cars squealed to a stop as we moved.



We'd just crossed the threshold of the parking garage when Dauntless opened fire, striking Brutus no less than three times with jabs of his Arclance, then turning his attention to Angelica.  The weapon could extend as far as he needed, elongating faster than the eye could follow.  White sparks flew as it slammed into the animals, but the effect was minor at best.  The Arclance was something between a solid and an energy, combining traits of both.  It could hit hard enough, with an electrical charge to it to boot, but I suspected that using it on the dogs wasn't so different from using a hand taser on a bull elephant.  They were too big, too tough.



Finding he wasn't having much effect on the animals, Dauntless aimed for us.



Regent disrupted Dauntless' aim, and the Arclance ripped over the windows of the building above the parking garage, bringing a rain of glass shards down on us as we made our way past the gate and into the garage.



Armsmaster exited the alley and spotted us.  Intent on closing the distance, he sent his grappling hook out to catch the metal `do not pass if you are above this height' bar above the door of the parking garage.  The second the points of the hook closed around the bar, Armsmaster started reeling himself in, his metal boots skidding across the roadtop.



Bitch whistled, hard, and pointed to the bar.  Judas lunged for it, catching both bar and grappling hook in his jaws.  The chain holding the bar up snapped as Judas pulled, and Armsmaster's skid was interrupted as Judas pulled back on the chain that extended between them.



Armsmaster shifted to a run, managing to keep his feet under him as his trajectory changed.  He extended his stick arm, and I saw a spray of blood fly from Judas' mouth, the dog rearing back in reaction.  Judas let go of both the bar and the hook and backed away several paces, growling.  As the hook retreated, I saw it wasn't in its grappling hook form, but the usual halberd-top, complete with blade, spearpoint, and no small amount of blood.



Armsmaster maintained his momentum, finished reeling in, then send the ball out again, his weapon back in flail-style.  He brought Judas down, then brought the flail in a wide sweep to keep the other two dogs at bay.  Dauntless continued his approach, stopping just behind and to the side of Armsmaster.



``My mapping program says there's three ways out of this garage,'' Armsmaster informed us, ``The doors on the other two exits are locked, and I guarantee you won't have time to crack the lock or break down the door before I catch up with you.  No more tricks, no more-''



He stopped mid-sentence, whipped his head to one side, then the other.  ``Wha-''



And then he disappeared.



A yellow painted concrete pillar, the sort that was used to keep cars from parking in front of the stairwell doors, or to protect the ticket vending machine from any collisions, appeared in his place.  It hit the ground hard, then toppled onto its side.  At the same time, we heard a series of heavy collisions from behind us.



A steel giant with massive hands and a spout on its back that was spewing volumes of gray-black smoke had one hand closed around Armsmaster.  Repeatedly, methodically, it slammed Armsmaster against the hood of a car.



Ballistic, with his football player build and angular body armor, stepped out of the shadows between the cars to Dauntless' left, just by the entrance.  A girl I recognized but hadn't yet seen in person emerged from the right.  She wore clown makeup and a jester's cap, with a teal and orange skintight costume complete with coattails.  Bells jangled from the tips of her cap, her coattails, her gloves and boots.  Circus.  Her costume, makeup and color scheme were different every time she went out, but the theme was always more or less the same.



Dauntless moved to retreat, but Sundancer intercepted him, stepping around the front of the building and placing her miniature sun in the center of the entryway to bar exit.



I didn't have enough bugs to contribute, and had too little of an idea of what was happening, besides, so I stayed put and watched as the rest of the scene unfolded with surprising speed.



Armsmaster fought his way out from the giant metal hand, but found himself dealing with not just the machine, but a creature from the black lagoon, replete with crustacean armor and octopus tentacles in the place of arms and a face.  He managed to fend them off for a few brief moments, until he swung his weapon at the octopus creature and wound up with a car bumper in the place of the Halberd.  He didn't have a grip on the bumper as it materialized, so he fumbled and dropped it.  Before he could recover from his surprise or his lack of a weapon, he found himself caught in the mechanical hand.  The steam powered giant resumed his methodical thrashing of Armsmaster against the now-battered car, with the octopus-crab man standing patiently by.



Circus threw a handful of knives at Dauntless, only to have them deflected when he encapsulated himself in his forcefield-bubble.  The second the bubble went up, though, I saw Ballistic reach down to touch the car parked beside him.  When he used his power on the car, you didn't see it move.  Rather, in the blink of an eye, it was gone from where it had been, abruptly in a position where it was virtually wrapped around the upper half of the forcefield.  It started rolling off the other side before the forcefield gave way, then dropped to the ground a scant foot from Dauntless.



Circus hadn't stopped moving.  As the car hit the ground, her feet found positions on the undercarriage, and she was up and over, leaping toward Dauntless.  She brought her hands back, and at some point I couldn't see her hands, she got a two-handed grip on a large, colorfully painted sledgehammer, colored streamers trailing from it as she swung it in Dauntless' direction.



Circus was one of those capes that had a whole pile of very minor powers.  The ones I knew about were some minor pyrokinesis, the ability to deposit items into thin air, to retrieve those items just as easily, and greatly enhanced coordination and balance to round off the package.  She was one of the more successful solo villains around Brockton Bay, a burglar and thief both quick and versatile enough to win or slip away if she crossed paths with a hero.  If I remembered right, she'd been offered a position on the Undersiders and had vehemently refused.



Which raised the question of what she was doing \emph{here}, with the Travelers.



Dauntless parried Circus' sledgehammer with his Arclance, and the Sledgehammer was gone in the next second, as though it had never existed.  At some point in the meantime, though, she'd managed to slip a lit torch into one hand.  She raised it to her mouth, and blew a large cone of flame in Dauntless' direction.



He staggered back from the torrent of flame, raised his shield, and widened it into a forcefield bubble again.  Less than a second after the shield went up, Ballistic sent another car flying into it with enough force that the car rebounded into the ceiling, back to the ground and into the other side of the parking garage.  The shield failed, flickering out of existence, and Dauntless reeled.



Circus took the chance to close in, torch gone, sledgehammer out.  What followed was a brutal takedown, as Circus swung the sledgehammer twice, making it disappear rather than heftting it back for the next swing, which made the assault that much more relentless.  She ducked low to avoid his Arclance, then spun in a tight circle as she sidestepped around him.  As she rotated her body, the sledgehammer made an appearance once more.  She carried through with the spin with the weapon in hand, driving it hard against the center of Dauntless' armored chest.



Dauntless fell, and the conflict was abruptly over, silent but for the crackle of Sundancer's miniature sun, and a single honking horn outside.



The two giants, the machine and bizarre sea creature, approached us, with Trickster lagging behind them.  I could see the machine-guy's face, a heavy cheeked caucasian with acne-scarred cheeks and long hair pulled back into a greasy ponytail, the upper half of his face covered in a metal mask and goggles, and now I could place him.  He was Trainwreck, a fairly thuggish villain that hadn't made much of a name for himself.  I couldn't say whether that was a suit or actually his body.  For all I knew, he was some sort of coal-driven cyborg, or an unfortunate individual that'd been transformed by his powers much in the same way Newter and Gregor had.



And of course, that left the odd one out, the sea-creature, who could only be Genesis, from the Travelers.



Trainwreck dumped a beaten and bloodied Armsmaster to the ground, beside Dauntless.  He took a second to examine the Halberd, which he held in his other hand, and then snapped it in his hands and squeezed the remains in his metal fist.  He dumped the resulting debris over the unconscious heroes.



I looked across the assembled group.  The Travelers and two villains that had never, as far as I knew, been on a team.  Nobody was saying anything.



A smooth, self assured voice broke the silence.  ``I assumed, Tattletale, that when you asked to meet with me at the conclusion of your task, that you wouldn't be bringing the heroes with you.''



A soldier in kevlar and a black balaclava was holding the stairwell door open for Coil.  Dressed in the same black bodysuit with the image of a white snake arranged across it, Coil joined us, walking slowly, his hands clasped behind his back, taking in the scene with an appraising eye.  Two soldiers followed behind him, guns in hand.



\emph{Coil}.  I felt my pulse quicken.



Tattletale made a pained expression.  ``Sorry.''



Coil glanced around some more, then seemed to come to a decision, ``No.  I don't think there's anything to apologize for.''



He paused, and all I could think was \emph{this is it.  I've got what I need}.



Coil spoke, more as though he were musing to himself than any of us, ``I was feeling theatric.  The plan was for the Travelers, Circus and Trainwreck to step out from the shadows as I made an impressive entrance.  A shame it didn't play out, but I suppose it had a tactical benefit.''



``Guess so,'' Tattletale grinned.



``Well, it seems you were successful tonight.  Good.  There are no more pursuers?''



``Nope.''



``Emergency response?  Other heroes?''



``All at least two and a half minutes away, I think.''



``Then we'll take our leave.  Undersiders, Trickster, I have a ride prepared, and I would like you to join me.  I believe we have much to discuss.''





