





We didn't dally, stopping only to let Bitch direct her dogs into three separate vans Coil had waiting at the back of the garage.  Once that was done, we all rushed to the vehicle Coil had waiting, an armored limousine.  It wasn't too different from a regular limousine, but the sides and top were flat, and the front end was squatter.  All in all, it gave the general impression of something exceedingly solid.



I wondered if it was too conspicuous.  It was distinctive enough that it Could make us too easy to track.  Coil didn't seem like a stupid guy, though, and time was short enough that we couldn't afford to take the time to debate it.  I climbed inside after Grue, keeping my mouth shut for the time being, and my eyes open for details.



The interior was all black leather, the windows tinted dark.  Coil's black costume against the black background made him rather hard to make out as he settled into a chair at the far end, his back to  the driver's seat.  If I squinted a little, it looked like only the snake stenciled on his costume was there, hovering in empty space.  We seated ourselves on the leather cushioned bench that lined one side of the limousine.  Trickster, the only Traveler to come with us, sat at the far end, facing Coil.



``My dogs-'' Bitch started.



``Will be taken care of, I assure you,'' Coil replied.  ``You will find your dogs and the vans you used to arrive awaiting you when you depart.''



Bitch pursed her lips, looking angry, but didn't say anything.



``I wish,'' Coil told us, ``To perform a small demonstration.  Because I would prefer to establish a few things before I move on to discussing the larger picture.''



He reached into a cup holder to his left and retrieved a roll of quarters.  He undid one end of the roll, then doled out a number of quarters into his palm.  ``If you would catch these and place them on the backs of your hands.''



He flipped a coin in Tattletale's direction.  She caught it and slapped it against the back of her hand, ``Heads.''



``Heads,'' Grue said, as he caught the next.



Coil double checked I was ready to catch it, then threw it my way.



``Heads,'' I spoke, as I slapped it down.



And heads again for Bitch and Regent.



I leaned forward, reached behind me, and retrieved my coinpurse.  I found a silver dollar, showed Coil, and then flipped it.  I caught it and slapped it down.  Heads.  I nodded.



``Probability manipulation?'' I asked him, ``Enhanced luck?''



He shook his head, ``No.  Just the opposite, Skitter.  I control \emph{destinies}.  I decide outcomes.''



``That still sounds like probability manipulation to me,'' I said.



Tattletale leaned forward, to look past Grue and face me, ``No.  Well, it is, but only in the biggest, bluntest sense.  But I can vouch that he's telling the truth, vague as it is.''



``When I asked what his powers were, at the meeting, you said you didn't know,'' I accused her.



``No,'' she shook her head, ``I said I \emph{couldn't say}.  Which is true.  One of the contingencies for my getting to be part of the Undersiders and get the funding he offered was that I would keep the details a secret, and I've got to do that until he says otherwise, sorry.''



Coil placed his elbows on the armrests and steepled his fingers in front of his mouth, or where his mouth would be if his mask showed any part of his face.  ``I feel that keeping potential enemies in the dark is a necessity.  To those ends, rather than risk having her as an enemy, I sought out your Tattletale and hired her, with enough incentive to keep her loyal and silent on the matter.''



``And us?'' Grue asked.



``I won't mince words, Grue,'' Coil answered, ``My choice to form the Undersiders was a gambit.  If you failed, got yourselves killed, injured or arrested, then that simply meant there would be less parahumans in this city for me to be concerned about.  That isn't to say I didn't assist you or that I attempted to steer you towards failure.  I did just the opposite.  All I mean to say is that I was prepared for the eventuality.''



Grue tilted his head slightly, ``And if we succeeded?''



``Then you naturally find yourselves sitting here, proven to be capable,'' Coil leaned back.  ``Worthy to hear my proposal, as the Travelers already have.''



``I can't help but notice you didn't test them the same way you tested us,'' Grue spoke, ``We've worked for you for nearly a year.''



``The Travelers have an established track record.  With this in mind, I contacted them and requested they come to Brockton Bay.  They heard my offer, and I was hoping Trickster might give his reply tonight.''



All eyes turned to Trickster.  He didn't hurry to reply.  He reached into the fold of his jacket, found a pack of cigarettes, tapped one out, placed it inside the mouth-slit of his mask and lit up.  He placed one hand on his hat to keep it in place as he rolled down the window to blow the smoke outside.



``If you're not bullshitting, if you're making a good faith attempt at providing a fix, we're in,'' Trickster spoke, not looking at Coil.



``Excellent,'' Coil replied, not twitching a muscle.  There wasn't an iota of surprise there.



``Fix?'' I asked Trickster.



``That guy,'' Trickster tilted his head in Coil's direction, ``Is offering my team a temporary solution to an ongoing problem, with promises that he's going to look into a possible permanent fix.''



``Vague,'' Regent spoke.  Trickster shrugged.



I couldn't quite get a sense of these guys.  I spoke up, ``This wouldn't have anything to do with what your teammate said about you guys pulling a ridiculous number of jobs, like you're trying to fill a bottomless pit with cash?''



He turned to one side to let out a long exhalation of smoke, then answered, ``My \emph{teammate }needs to keep her mouth shut about private business.''



Which, in no uncertain words, meant I should drop the subject, and that I was probably right.  Probably not my best call, raising a subject pretty much guaranteed to touch a nerve.



``So,'' Grue spoke to Coil, ``You've provoked our curiosity, which I'm sure was your intent.''



``Yes.  First off, let me show you what I desire,'' Coil spoke.  He touched a button beside the cup holders to his left, and the windows rolled down.  I looked outside, and saw the darkness of a tunnel.  As we left the tunnel, we found ourselves overlooking the rest of the city.  The bay and the city both were spread out beyond us, a cityscape lit up by constellations of orange-yellow and white dots and the faint light of the moon above.



I looked back to Coil, and saw him gesturing to the open window.



``The city?'' I asked him.



``The city, yes.  Desiring to take over the world is not only cliche, but unrealistic,'' he replied, his voice sibilant, smooth.  ``I will, for the time being, content myself with seizing this city for myself.  Cliche still, I might admit, but rare few do even \emph{this }with any measure of success\emph{.}''



``Isn't it kind of obvious you're trying to do that already?'' Regent asked him.



``Perhaps, but contrary to popular expectations, I do not aim to limit my control to the organized crime of Brockton Bay.  I would control \emph{everything}.  Government, courts, law enforcement, business, and much more.''



``Ambitious,'' Grue spoke.  I thought I might have heard a change in his tone of voice.  Doubt?



``Quite.  But rest assured, Undersiders, I am already moving into my endgame.''



``Endgame?'' I asked.



``\emph{Think}, Skitter.  Who are the major players in this city?  What has changed?  The ABB is wiped out, with the very plan I proposed at the meeting.  Empire Eighty-Eight is reeling from the plays I made today, and I fully expect to finish them off in the coming weeks, hopefully with the assistance of you, the Travelers, and my other recruits.  The Wards and the Protectorate are in a tenuous position, now.  I took steps to ensure the public knows their heroes played only a partial role in stopping the ABB, and your actions tonight served to shake confidence in them further.  If the matter is pushed further, I expect there will be a restructuring of the group structure.  Perhaps members will be exchanged with other nearby Protectorate groups, someone else might be put in charge, new rules, regulations and quotas put in place.  Whatever the case, it will be some time before they regain their footing and re-establish their reputation.  By the time this occurs, I will be settled in my new role.''



He let that sink in.  ``Who else is left?  New Wave isn't in a position to take control.  They are powerful but too controversial, with even less trust from the public than the Protectorate.  The Merchants under Skidmark's leadership are too weak and self centered to make a serious play.  Faultline's group is mercenary, and conservative use of my power has made me an exceedingly wealthy man, leaving me the option of purchasing her cooperation if and when it is necessary.''



``There are scarce few who are in a position to impede me, as I make my play, and I'm not only speaking of capes.  I've quietly been purchasing properties throughout the Docks and will aggressively purchase more in the final stages of my plan.  Two of the three mayoral candidates for this June's election were bought and brought to this city by me, much as I purchased my elite soldiers to aid me in controlling the streets and hampering the Empire's business.  The city council has its elections in September, I will have similar agents placed throughout by then, as well.  When I say I am nearly finished, I am not speaking in ambiguities.  I am saying that the dominoes have been set up and the first of them are already falling.''



\emph{Well}, I thought, \emph{there goes any doubt I had about the Protectorate not caring what was up with the Undersider's sponsor}.  Shit.  Was he really that close?



``Leaving only you and your role in this,'' Coil finished.



``Which is?'' Grue inquired, a challenging note in his voice.



``Taking over this city is pointless if I do not \emph{keep} it, Grue.  I hand picked you Undersiders because I needed allies who were comfortable being situated in the North end, the Docks, the Boardwalk, the Trainyard, the outskirts to the North.  I picked you because I saw you had potential, yet you were not so high profile as to demand the immediate attention of authorities.  This freed you to be overlooked until you were more established.  It allowed you to grow both practiced and comfortable as a team, and to establish a reputation for yourselves.  In my efforts against Kaiser, I have not only been whittling away at his Empire, but I have worked to keep him occupied so you would not be sandwiched between two major factions in the early stages of your group.  You had only the ABB to deal with, and you held your own for nearly a year.  Skitter joining your group was sufficient to tip the balance.''



``So.  If you accept this deal, I would have you control the Docks and the surrounding area.  You're not overly disliked, you've proven yourselves resourceful and capable.  I would have you guard against any parahuman trespassers and squash any gangs or groups in your territory, should they not submit themselves to my command and control.  If this project proved to be a success, I would have you be my agents in expanding to nearby \emph{cities}.  But I digress, that is long term, only a possibility.''



``And what do we get in all this?'' Regent asked.



Coil replied, ``I expect that wealth and power go without saying.  Beyond that, I leave it to you to name your terms.  As I explained what I desire, I leave it up to you to decide what you would ask for, in exchange for your cooperation.''



Nobody hurried to reply.  We exchanged glances with one another, trying to gauge each other's reactions.  Trickster finished his cigarette, tossed it out the window and rolled the window up.



Coil broke the silence, ``Bitch.  I am aware of your collection of dogs.  More than one isolated building containing strays and dogs due to be euthanized.  Animals that you rescued, retrieved and gave shelter.''



All attention turned to Bitch.  She looked angry, opened her mouth to speak, but Coil interrupted her before she could.



``No.  I would not interfere with your business.  I \emph{respect} your passion.  But at the same time, I know it likely pains you, that you have only so much time to spare, to visit these locations, to feed these animals you have rescued and give them the individual attention and care they need.''



Bitch glared at him.  If looks could kill.



``I could provide the resources you need, to fully equip the buildings and make them comfortable for the dogs.  Assistants to care for the animals and work under you as you see fit.  I would have the city give the same sort of funding to anyone who adopts a sheltered animal that is provided to foster parents, with oversight, of course, to ensure that the animals are being properly cared for, that the system is not gamed.  There would be no more dogs cooped up in shelters, awaiting euthanasia.  What would you say to that?''



``I'd say you're fucking with me.''



He didn't press the issue, instead, he turned to the next member of our group.  ``Regent.  A hard young man to please, because you grew up wanting for nothing, and you expect largesse, luxury and idle entertainment as a matter of course.''



``What do you know about how I grew up?'' Regent challenged him.



``I know what the Protectorate knows.  Not long after Lung was brought into custody, Armsmaster began pushing for details on your group.  Staff at the PRT offices were tasked with looking through old criminal records and reports of lesser known parahumans, trying to find parallels.  Find if perhaps a supervillain in another area perhaps moved to Brockton Bay, changing their names, costumes and methods.  They found \emph{you}.''



``Ah,'' Regent leaned back in his seat.  ``Shit.''



``So I know who you are.  I know that you went out of your way to get out from your father's thumb, and that it's quite likely that a part of you is driven to prove yourself to him, to pursue success, power and status in our circles.''



``His father?'' I asked.



``Not my story to tell,'' Coil waved a hand, ``I leave it for Regent to share at a later date, if he chooses.  All I mean to say is that I can give you that, Regent.  Status and notoriety, perhaps enough to rise above your old man.''



Regent nodded once, but didn't say anything.  I would have liked to see his expression behind his mask.



``You must understand, Undersiders, I do not use fear as Lung did, or manipulation as Kaiser does.  I would have you work alongside me because you know I am the person that is best equipped to provide what you desire, and that nobody else can or will give you a better offer.''



``Which sounds nice, sure,'' I countered.  Could I poke holes in this plan, maybe derail it? ``But I haven't quite forgotten that you \emph{just} told us you were fully prepared for us to screw up somewhere along the way, and that you would have been perfectly okay with it happening.  You would've shrugged, said `less capes to deal with' and you would have dropped us and walked away.''



Coil nodded, ``This is true.''



``So if we screw up later, it's going to be the same thing?''



``No,'' Coil spoke. Then he paused for a moment.  ``I understand your concern, but I have already informed you of a great deal, here.  If you were arrested, or if half your team perished in action, it would be dangerous to abandon you, because you could divulge key information.  This will continue to be the case.''



I nodded, slowly, ``Except you could provide false information to us, or stop providing key info.''



``Look to Tattletale for the answer to that.  I may have purchased her assistance, but I expect you consider her a friend, and vice versa.  You could, I hope, trust her to verify that what I tell you is truth, and to know more about my plan that I divulge, in any case.''



So if I wanted to argue the point further, it'd look like I didn't trust Tattletale.  I wasn't sure I liked that, but I nodded.  ``Alright.''



``Skitter,'' Coil spoke.  ``I came prepared, tonight, with offers in mind for the rest of your team.  I can help care for Bitch's collections of rescued dogs, and help ensure less animals need rescue in the future.  Grue is relying on me for a personal matter, and he knows that my taking power can only ensure that things go his way without difficulty. You, and you alone, Skitter, have me wondering what you desire, at the end of things.''



Tattletale, to my left, leaned forward again, interest clear on her face.



I had to be convincing.  No way was I going to let something slip past the radar and alert Tattletale \emph{now}.  So I gave it a serious think.



I kind of hoped someone would break the silence while I took the time to consider, maybe even distract from me, but nobody did.  Everyone patiently waited, putting me at the focus of all attention, a spot I hated being in, in or out of costume.



``The city,'' I replied, being careful to be as genuine as possible, to avoid alerting Tattletale, ``You want to control it.  Fine.  I want you to make it \emph{work}.  Fix up the Docks so they aren't a shithole.  Give people work.  Clean up the drug trade, or the hard drugs at least.  Straighten out the asinine bureaucracy of the government and schools and all that.  That sort of thing.''



Coil shook his head, ``Not something I can offer you in good conscience, dear Skitter.''



He raised his hand to stop me before I could open my mouth.  Not that I was going to, but he did.  ``What you're talking about, I already intended to do, in large part. To give it to you as a gift would be little different than offering you an amount in cash, when I already intend to give you as much money as you require.''



``So you're going to improve Brockton Bay,'' I said, carefully.



``Don't get me wrong.  I will not claim to be a good person – I assure you I am not.  \emph{That said}, you are likely to discover I am a proud man.  I would consider it a catastrophic failure on my part if this city did not thrive under my rule, a tremendous blow to my ego.''



I nodded.



He continued, ``Our desires on individual subjects may differ, however.  I would argue there will always be crime, always be drugs.''



``I'm not saying there won't.  I'm just saying that there's room for improvement.  When I was in grade six, more of my classmates could explain what a K-hole was than name a dozen countries.''



``I am not promising quick fixes, Skitter.  What I will tell you is that individuals like yourselves would control territories and be responsible for maintaining your own kind of order in those areas, with whatever means you saw fit.  Over time, people would adjust to this, crime rates would decrease.  I would simultaneously be controlling the flow of product into the city, reducing the distribution of the most problematic drugs, those that would lead to the most societal decay and crime, while making other, more benign product available in their place.  Crime and drugs cannot be conquered, but they are animals I believe I can tame.''



``And the city itself?'' I asked.  I thought of my dad, ``Fixing the ferry?''



``Yes.  Rest assured, if you were to accept my offer, I would fully expect you to contact me and speak up at any time you felt I was not following through in any department.  I might be a proud man, but I would rather you injure that pride, even provoke it intentionally, rather than let me be complacent.''



I nodded once, slowly.



``I have said my piece, then.  I leave you to consider it, Undersiders.  I recognize that this is not what you signed on for, in the beginning.  I know it might not have the same appeal in the scope of costumed hijinks, and I'm prepared for the fact that that this might lead you to refuse this offer.  All I hope is that if you do refuse me, if you decide you are more comfortable as simple uncommon criminals, that our prior arrangement will stand.''



``You've invested this much in us, and if we say no, we can just walk away?''  Regent asked him.



Coil spread his hands a bit, ``What would you see me do?  Murder you?  Threaten you?  Orchestrate an arrest?  There is no guarantee any attempt on my part would be wholly successful, whatever I chose, and you may count it as a compliment that I would not want \emph{any} of you escaping the attempt and coming after me as a dedicated adversary.''



He knocked on the window behind him.  Immediately, the limousine slowed down and pulled over.  As I glanced outside, I saw we were in the Docks.



``Think on the subject.  Discuss it and get back to me with your reply, the sooner the better, no later than a week from now.  Tattletale, it should be obvious, but I formally free you from all stipulations in your contract requiring you to keep my identity as your sponsor private.  You may give my contact information to your teammates.''



``Sure thing,'' Tattletale replied.



``And before I forget, I arranged individual accounts for each of you with a supervillain banker by the name of The Number Man, as paying for tonight's job in bills, naturally, was unfeasible.  My men will provide you with your account information and the instructions for accessing these accounts as you retrieve your dogs.''



Grue extended a hand, ``I'm not sure what we'll do, whether we'll take this deal, but it's been good working with you thus far, and I hope to continue.''



Coil took Grue's hand and shook it, firm, ``Likewise, Grue, Undersiders.''



We departed the vehicle.  We were on the West end of the Docks, judging by how far the water was, and how close we were to the mountains that surrounded the city.  Parked behind the limousine were three vans, each with two of Coil's soldiers standing by, alert.



As we walked by the end of the armored limousine, a soldier passed out envelopes to each of us.



We continued walking, and Bitch opened each door we passed, letting the dogs out.  They were smaller, now.  Judas, the tallest, only came up to my shoulder.  Their external muscle, wet and wrinkled, hung off them like excess skin on a person who had lost a great deal of weight.  The interiors of the vans were spattered with more excess flesh, blood and bone that had been shed.  The final stage would be the dogs shucking off the last of the excess mass, revealing their normal shapes nested deep within, dry within a membrane, virtually untouched by the injuries they had sustained over the night.



As the last of the dogs, Angelica, was released and the vans and limousine pulled away, we headed back to the loft.  Each of us too busy sorting through our own thoughts and dilemmas to be distracted with conversation, so it was remarkably quiet.



\emph{I have it.  I've got what I need}.



I just didn't know how I felt about it.





