





Dear Miss Militia\ldots



Was it wrong to start with Dear?  Was that implying more friendship or intimacy than there was?  Would it seem taunting?



Miss Militia, we met earlier tonight\ldots



No.  If I went that route, she might throw it aside alongside all the other fan mail she got.



Miss Militia, you know me as Skitter, but you don't truly know me\ldots



Better, but I didn't like the tone.  I'd leave it as is, move on, and come back to it later.



\emph{\ldots}You see, I'm not a villain, despite\ldots



Despite what?  Despite the fact that I'd terrorized and hurt a lot of innocent people?  Despite the fact that I'd nearly killed Lung and later cut his eyes out?  That I had nearly two hundred and eighty thousand dollars in illegitimate money to my name?



I shivered, pulled my hands from my pockets and did up my sweatshirt to cover my exposed stomach.  After we'd arrived at the Loft, Brian had suggested that we were all too tired to discuss Coil's proposal, so we tabled all discussion until the morning.  I was glad for the excuse to avoid hearing or seeing anything that might make this any harder.  Besides, I'd promised my dad I would be home tonight.



It was past nine, so the bus from the ferry was only arriving every ninety minutes.  I'd figured it was better to walk home than wait.  I could use the stretching, too, given the abuse my body had sustained while I was riding Judas.



Sticking my hands back in my pockets, I returned my thoughts to how I'd word my letter to Miss Militia.  Scratch `despite'.  Another approach, maybe?



\ldotsBelieve it or not, my intentions all along have been good.  I joined the Undersiders in the first place to assist \emph{you}.  To assist this city\ldots



Was that entirely true?  No.  If I was being entirely honest with myself, part of the reason I'd joined and stayed with the Undersiders was because I had been lonely.  What if I offered some honesty?



\ldotsIt caught me off guard just how easy it was to like them.  I was in a bad place, and they accepted me.  So writing this email to you is difficult.  But it is necessary.  In the end, I decided to go this route because it serves the greater good\ldots



That was what I had told myself, earlier today, before we left for the job.  That sticking with those guys would pose the greatest risk to innocents, that it would eventually lead to someone getting caught in crossfire, or me getting arrested for something serious.



But now I had Coil's agenda to consider.  Was he really being honest about how he planned to help this city?  I had no reason to believe he was lying, and Tattletale was vouching for him.  But at the same time, Coil's motif was a \emph{snake}, and Tattletale had hedged the truth and misled me before.



Question was, was I taking this route because it served the greater good?  No.  Or at least, I wasn't sure enough either way for it to be the reason I was doing this.



\emph{Why was I doing it, then?}



It had been a hard question to answer hours ago, and it was doubly hard now.  Enough that it spooked me.  How had I gotten to this point?



I was put in mind of a time I'd sat in on one of my mom's university classes.  I couldn't have been older than ten, my dad had been busy and my mom hadn't been able to find a babysitter.  So I'd been precocious, proud as hell to be sitting in that English lecture with the teenagers and twenty-somethings and understanding what my mom was saying.  We'd even read the book together, over the prior few weeks, so I knew the material.  Oranges are not the Only Fruit.



While I'd been sitting and listening, an older man had come in and sat next to me, in the back row.  In a kind voice, he'd murmured a comment about how my mother was an excellent professor.  Then, a few minutes later, when I got up the courage to raise my hand and answer one of her questions, he'd complimented \emph{me}, got up and left.  All my pride in myself and my mother aside, what had struck me about the encounter was the man's hair.  A ridiculous comb-over.



After the class was over and my mom had been taking me home, I mentioned the man, and she'd identified him as the head of her department, her boss.  Then I brought up the comb-over and how bad it looked.



``Look at it from his perspective,'' she'd explained.  ``Maybe, a long time ago, he started to lose a little hair, but he could brush it to one side in a way that made it not show so much.  Every year that passed he brushed his hair over a bit more.  It was gradual, something he slowly got used to, seeing it in the mirror every morning and every night.  Lots of small steps.''



``Why doesn't someone point it out?''  I'd asked her.



``He doesn't have anyone to point it out for him,'' she had replied, ``And anyone who knows him well enough doesn't want to hurt his feelings, even if it might be better in the long run.''



``You could,'' I'd told her.



So she had, later that week.  Ripped off the band-aid for the old head of the English department.  According to her, he'd gotten a haircut, then thanked her at a later date.  That event and what my mom had done afterward always stuck in my memory.



I swallowed past a lump in my throat.  It always caught me off guard, just how frigging much I missed her, when I thought about her.  I'd give \emph{anything} for a thirty minute conversation with her, right this moment.  I didn't have the slightest doubt in my mind that she could have made sense of everything, put things into terms so simple that working it out looked \emph{easy}.



I had to stop, look up, blink back the tears in my eyes, and take a deep breath before I moved on.



Was my situation the same as the old man's?  Had I let myself gradually slip into a bad spot, because of my lack of perspective beyond what was going on inside my own head?



I hadn't been thinking about this clearly.  I was still confident enough I could send that email, make the call\ldots but before I did that, I had to get my thoughts in order.  Composing the letter in my head wouldn't work, I needed the words on my computer screen in front of me, concrete words in black and white.



I walked around the back of my house and reached into my pocket for my keys.  Before I could get them, my dad opened the door.



``Taylor.  It's good to see you safe and sound.''  My dad looked tired, years older than the last time I saw him.



I gave him a brief hug, ``Hi, Dad.  You got my message, saying I'd be late?''



``I did.''  He shut and locked the door behind me.  ``What happened?''



I shrugged as I pulled off my sweatshirt, made sure my pepper spray, phone and keys were all in the pockets, then hung it up by the door.  ``Nothing big.  I was at Brian's, helping him put furniture together, then his sister and his sister's social services caseworker came without any warning.  I couldn't find a way to leave without it being kind of awkward.''  \emph{Which did happen, pretty much, just at an earlier time.}



``I see,'' he murmured. ``Were you two alone?''



``No,'' I lied, to stop him from getting the wrong impression.  ``At least, not for long.  Lisa left a few minutes before the caseworker dropped by.''



``And you have a new shirt, I see.  It's nice.''



``Lisa's,'' I fibbed, squirming a little under the scrutiny.



``Ah,'' he nodded.



``I'm going to go to my room, if that's alright?  I'm kind of wiped.''



My dad shook his head, ``I'd rather you stayed to talk.''



Not what I wanted to do.  My mind was jammed with enough crap and internal debates that I didn't want to worry about concocting more lies for my dad.



``Can we do it tomorrow morning?'' I offered him, retreating toward the door to the front hall, pressing my hands together in a pleading gesture. ``I really need to sit at my computer for a minute and organize my thoughts.''



I pushed on the door and it didn't open.  Strange.  I tried the doorknob, and it didn't help.



``Door's jammed,'' I said.



``Door's locked, Taylor.  So is the door to the living room.''  My dad answered me.  When I looked at him, he showed me the old fashioned key in his hand.



As I watched, he pulled out two chairs from beside the kitchen table, placed one in the middle of the room, then placed the second chair against the back door and sat down in it.



``Sit.''



``Dad, tonight's not really-''



``\emph{Sit.}''



My heart dropped out of my chest.  Or at least, it felt like it.  I felt an ugly sour feeling in my stomach.



``I talked to your school today,'' he informed me, confirming that ugly feeling.



``I'm sorry.''



``You've missed nearly a month of classes, Taylor.  \emph{Three weeks.  }You've missed major tests, project due dates, homework\ldots they're saying you might fail, if you haven't already.''



``I- I'm sorry,'' I repeated myself.



``I could maybe understand, I know what you've been dealing with, except you didn't just leave me in the dark.  You \emph{lied} to me.''



I couldn't form the words for another apology.



``I called the school to get an update on how you were doing, and they said you hadn't been to class in some time, and I didn't know what to do.  I just- I felt completely lost.  I called your Gram.''



I winced.  Gram was my mom's mother, an austere woman who'd never fully approved of my dad as a match for her daughter.  It wouldn't have been easy for him to make that call.



``She convinced me that maybe I've been too focused on being your ally, and not focused enough on being your parent.  If she'd told me that a week ago, I would have hung up on her.  But after talking to your school, realizing how badly I failed you-''



``You didn't fail me,'' I told him.  I was caught off guard by how my voice broke a bit with emotion.



``I did.  It's clear that whatever we've been doing hasn't been working, if you're in this situation, if you can't talk to me.  No more secrets, no more half truths.  So we're going to stay here all night if need be.  I'll even call off work tomorrow if I have to, but we're going to talk.''



I nodded and swallowed, hard.  I still hadn't sat down in the chair he'd left in the middle of the kitchen.



``I, um, need to use the washroom.''



``Okay,'' he stood.  ``I'll walk you there, and I'll walk you back here to the kitchen afterward.''



``You're treating me like I'm a\emph{ prisoner?}''



``You're my \emph{daughter}, Taylor.  I love you, but I know there's something going on, and it's not just the bullying, or it's something to do with the bullying that you haven't mentioned yet.  I'm \emph{scared} for you, Taylor, because you're avoiding me and staying silent even if it means failing.''



``So you force my hand by making me your prisoner,'' I replied, letting anger and hurt creep into my voice, ``Do you think this is even remotely cool, after all the times I've been cornered by those \emph{bitches} from school?  I've got to come home to this bullying power-abuse shit, too?''



My dad answered me with the utmost patience, ``I hope you know that I'm doing this because I love you.''



I did.  Thing was, that didn't make it even slightly easier to handle.



``\emph{Do} you need to go to the bathroom, Taylor?''



I shook my head.  What I needed was to get out of this room.  I saw him purse his lips, knew he was aware I'd just been looking for an escape.



``\emph{Talk to me}, Taylor.''



``Don't feel like talking.''  I walked across the room to try the other doors, to the living room and basement.  Locked.



``Why are you so insistent on escaping?'' he asked.  I could hear the pain in his voice, which didn't make me feel any better.  ``Please, just relax, sit down.''



I felt the crackle of my power at the edges of my awareness, realized I was clenching my fists.  Why was it that the people I was supposed to be able to rely on were the people who turned on me, cornered me, made me feel the worst?  Emma, the school, Armsmaster, now my dad?



I kicked the chair, hard enough that it made a mark as it hit the fridge.  My dad's eyes went just a bit wider, but he didn't move or speak.  I could feel the tug of my power as bugs throughout my neighborhood began to move to my location.  I had to willfully cancel out the order to make them back off and return to their normal behavior.



Not feeling even remotely better after my abuse of the chair, I shoved the cookbooks and printouts off the shelf beside the fridge, letting them spill to the ground.  A picture frame that had been hidden in the middle of the pile broke as it hit the ground.



``Damn it,'' I muttered.  I still didn't feel better, and I was having a harder time keeping the swarm at bay.



``Possessions can be replaced, Taylor.  Vent however you need to.''



``Dad?  D-'' I had to stop for a few seconds until I felt like I could catch my breath and talk without my voice breaking up, ``Do me a favor?  Stay quiet for a bit and let me think?''



He gave me a careful look before he answered me.  ``Okay.  I can do that.''



With nowhere else to sit, I put my back to the wall under the bookshelf I'd just cleared and let myself sink to the ground, my legs making their protests felt as I brought my legs up against my chest.  I folded my arms, resting them atop my knees, and buried my face against them.



I knew it had been 9:24 when I got in.  By the time I'd suppressed the bugs, got my power under control and felt safe to raise my head, it was 9:40.  My dad still sat in the chair.



I let out a long sigh, quiet, then buried my face in my arms again.



What now?



\emph{Come on, Taylor.}\emph{You've faced down Supervillains in life or death situations.  You faced down Armsmaster earlier tonight.  Is it that hard to face your own dad?}



No.  Ten times harder.



But I had to face the problem the same way.  Catalogue my options, my tools at hand.  Physical violence was out.  So was using my power.  What did that leave me?



The situation was ultimately the same, I decided.  I still had to write that letter to Miss Militia, organize my thoughts.  Problem was, now I \emph{had }an additional thing to deal with.  I had to fess up to my dad about what I'd done.



I wasn't sure I could say it.  My throat was thick with emotion, and I doubted I could organize my thoughts enough to convince my dad that I'd done everything for the right reasons.  I'd open my mouth to tell him, stammer out the basics of it, maybe he'd even look concerned at first.  Then as I kept talking, failing to adequately describe what I'd done and why, I could see his face turning to confusion.  After that?  Disgust, disappointment?



A little part of me died inside at the thought.



I'd write it.  I raised my head abruptly, looked to the papers scattered around me.  I found a manilla envelope, the kind you put documents inside.  Then I found a marker.



Along the top of the envelope, I wrote the words: ``I AM A SUPERVILLAIN.''



I stared at those words on the brown envelope that rested against my legs.  Then I looked up at my dad.  He was reading a book, his right ankle resting on his left knee.



I imagined handing him the envelope as-is.  Just that one line.



``\emph{Fuck.}''  I muttered.



``Did you say something?'' my dad looked up from his book and reached over to put it down.



``It's okay.  Keep reading,'' I said, absently, annoyed at the distraction, still pissed at him for cornering me like this.



``Okay,'' he agreed, but he didn't look at the book for longer than three seconds before glancing up at me again, as if to check on me.  I tried to ignore him and focus on the envelope



What to write?  After a second, I began writing below the title I'd put on the envelope.



I like Brian and Lisa.  I even like Alec and Rachel.  But they're supervillains too.  I joined them with the idea that I would get details the Protectorate needed and then betray them.



I raised the marker and frowned.



Why was this so damn hard?



I put the cap on and nervously tapped the marker against my knee.  Thinking about stuff, trying to gauge my feelings, exploring my thoughts to see what it was that made that knot deep in my gut get tighter.



My dad?  Was I too conscious of what he would read, how he would perceive it?  Yes.  But it had also been hard to write when I'd been mentally writing it for just Miss Militia.  That wasn't the whole picture.



Was I scared of arrest?  No.  Well, I'd seen bureaucracy at work with school, I didn't trust the system, I fully expected to get screwed over somewhere down the line.  But that wasn't what was driving my choices.  It was something more personal.



The team.  Was I worried over how they would take it?  Over possibly having them as enemies?  Like Coil had said, there was no guarantee any action against them would be wholly successful.  Tattletale would probably be able to tell a PRT team was there before they could get in position, and the team \emph{was} good at making an escape in a pinch.  Then I'd have one or more enemies after me, who knew everything they needed and had all the tools to make my life a living hell.



Warmer.



It did have to do with those guys, and it slowly dawned on me what it was.



I stood, then walked over to the oven.



``Taylor?'' my dad spoke, quiet.



I folded the envelope lengthwise to hide the words, turned on the oven burner, then held the tip of the envelope to the flame until it ignited.



I held the burning envelope over the sink until I was sure my message was obliterated.  I dropped the remains of the envelope into the basin and watched it burn up.



I didn't want to send that email to Miss Militia because I liked those guys.  That wasn't the big realization.  What made me stand up and burn the envelope was the realization that I liked those guys, I was fond of them, I trusted them to have my back\ldots



Yet I'd always held myself at arm's length.



It was stupid, it was selfish, but I really, desperately wanted to see what it would be like to get to know Lisa, without worrying that she would find out my scheme.  I'd like to see what it was like to interact with her without having to censor myself out of fear that I'd provide that damning clue.  I wanted to get to know Bitch and Alec better.  And Brian.  I wanted to be closer to Brian.  I couldn't phrase it any better than that, because I didn't know if there would be any future with him beyond a simple friendship.  I didn't expect there to be.  It still mattered.



I'd let myself think that I'd tried a friendship with these guys, that I had grown as a person, so it was okay to go ahead with my plan.  But I hadn't.  I'd never let myself truly open up and connect with them, and I was realizing just how much I wanted to.



My reasons for going ahead with my plan were thinning out, getting harder to justify.  My reputation was probably in shambles, I'd made enemies of everyone that mattered, and I had a number of felonies under my belt.  As much as I might try to ignore all that and tell myself I was doing it for the greater good, my conversation with Coil had left me less sure.  That wasn't to say I believed him wholeheartedly, or that I thought he'd be as successful as he thought, but I was less sure.



Damn it, I wanted to hang out more with the Undersiders. Knowing I was out of reasons to justify sticking with the plan, all the crap that would come raining down on my head if I did go ahead with it, how much I'd loathe myself for betraying friends?  This little desire for a real, genuine friendship was enough of a nudge in that direction.  I could change my mind.  I wouldn't be sending any letters to Miss Militia.



I ran the tapwater over the smoking remains of the envelope, watched the remains get washed away.  I watched the water running down the drain for a long time after the last scrap of burned paper was gone.



I turned off the tap, stuck my hands in my pockets, and crossed the kitchen to lean back against the door leading to the front hall, glancing briefly at the handle and lock before I leaned against the door with my back to it.  I called some bugs from the living room, hallway and heating vents down the front hall and up to the door, into the mechanism of the lock.  Could they move the necessary parts?



No such luck.  They weren't strong enough to manipulate the door's internal workings, and any bugs that might be strong enough wouldn't fit inside.  \emph{Go away}, I told them, and they did.



Which left me no good way to avoid dealing with my dad.  I felt more guilty than ever as I looked across the room at him.  He looked so bewildered, so concerned, as he watched me.  I didn't have it in me to lie to his face again.



But whatever I did was going to hurt him.



I crossed the room and he stood up, as if unsure as to what I was going to do.  I hugged him tight.  He hugged me back tighter.



``I love you, dad.''



``I love you too.''



``I'm sorry.''



``You have nothing to be sorry for.  Just- just talk to me, okay?''



I pulled away, and grabbed my sweatshirt from the hook by the door.  As I crossed back to the other side of the room, I fished in the pockets and retrieved the phone.



I started typing out a text.



``You have a cell phone,'' he was very quiet.  My mom had died using a cell phone while driving.  We'd never talked about it, but I knew he'd thrown his out not long after the accident.  Negative connotations.  An ugly reminder.



``Yeah,'' I replied.



``Why?''



``To stay in touch with my friends.''



``It-it's just unexpected.  I wouldn't have thought.''



``It worked out that way.''  I finished the text, closed the phone and stuck it in the pocket of my jeans.



``New clothes, you're angrier, lying to me, missing school, this cell phone\ldots I feel like I don't know you anymore, little owl,'' he used my mom's old pet name for me.  I flinched a little.



Carefully, I replied, ``Maybe that's a good thing.  Because I sure didn't like who I was before.''



``I did,'' he murmured.



I looked away.



``Can you at least tell me you're not doing drugs?''



``Not even smoking or drinking.''



``Nobody's making you do anything you don't want to do?''



``No.''



``Okay,'' he said.



There was a long pause.  The minutes stretched on as if we were both waiting for the other to say something.



``I don't know if you know this,'' he spoke, ``But when your mom was alive, and you were in middle school, the subject of you skipping a grade came up.''



``Yeah?''



``You're a smart girl, and we were afraid you were bored in school.  We had arguments on the subject.  I-I convinced your mom you would be happier in the long run attending high school with your best friend.''



I coughed out a laugh.  Then I saw the wounded look on his face.



``It's not your fault, dad.  You couldn't have known.''



``I know, or at least, I have that worked out in my head.  Emotionally, I'm not so sure.  I can't help but wonder how things would have played out differently if we'd gone ahead with what your mother wanted.  You were doing so well, and now you're failing?''



``So I fail, maybe,'' I said, and I felt a weight lift, admitting it out loud.  There would be options.  I'd picked up enough that maybe I could still pressure the faculty to let me skip a grade.  I would be old enough to take online classes like Brian was.



``No, Taylor.  You shouldn't have to.  The staff at the school knows your circumstances, we can definitely get some exemptions made, extend deadlines\ldots''



I shrugged.  ``I don't want to go back, I don't want to beg and plead for help from those assholes in the school faculty, just so I can return to the same position I was in a month ago.  Way I see it, the bullying is unavoidable, impossible to control or prevent.  It's like a force of nature\ldots a force of human nature.  It's easier to handle, if I think about it like that.  I can't fight it, can't win, so I'll just focus on dealing with the aftereffects.''



``You don't have to give up.''



``I'm not giving up!''  I raised my voice, angry, surprised at myself for being angry.  I took a breath, forced myself to return to a normal volume, ``I'm saying there's probably no fucking way I'll understand why she did what she did.  So why waste my time and energy dwelling on it?  Fuck her, she doesn't deserve the amount of attention I've been paying her. I'm\ldots reprioritizing.''



He folded his arms, but his forehead was creased in concern.  ``And these new priorities of yours are?''



I had to search for a response.  ``Living my life, making up for lost time.''



As if to answer my statement, the back door opened behind my dad.  My dad turned, startled.



``Lisa?'' He asked, confused.



Lisa revealed the key she'd taken from the fake stone in the back garden, then placed it on the railing of our back steps.  Unsmiling, she looked from my dad to me.  She met my eyes.



I shoved my way past my dad, and he grabbed my upper arm before I was clear of the doorway.



``Stay,'' he ordered me, implored me, squeezing my arm.



I wrenched my arm free, twisting it until he couldn't maintain his grip, and hopped down the back steps, felt my knees ache at the landing.  Three or four strides away, I turned back in his direction, but was unable to look him in the eyes.



``I love you, dad.  But I need-''  What did I need?  I couldn't form the thought.  ``I, uh, I'll be in touch.  So you know I'm okay.  This isn't permanent, I just\ldots I need a breather.  I need to figure all this out.''



``Taylor, you can't leave. I'm your \emph{parent}, and this is your home.''



``Is it?  It really doesn't feel like that's the case, right now,'' I answered.  ``Home's supposed to be a place I feel safe and secure.''



``You have to understand, I didn't have any other options.  You were avoiding me, not talking, and I can't help you until I get answers.''



``I can't give you any answers,'' I replied, ``And you can't help anyways.''



He took a step forward, and I quickly stepped back, maintaining the distance between us.



Trying again, he told me, ``Come inside.  Please.  I won't press you any further.  I should have realized you weren't in a place where I could.''



He took another step toward me, and Lisa took a little step to one side to get in his way, as I backed up again.



``Lisa?'' My dad turned his attention to her, looking at her like he'd never seen her before.  ``You're okay with this?''



Lisa glanced between us again, then carefully said, ``Taylor's smart.  If she's decided she needs to get away and work stuff out for herself, I trust it's for good reason.  There's plenty of room for her at my place.  It's not a problem in the slightest.''



``She's just a kid.''



``She's more capable than you give her credit for, Danny.''



I turned to leave, and Lisa hurried to catch up with me, putting an arm around my shoulders as she reached my side.



``Taylor,'' my dad called out.  I hesitated, but didn't turn around.  I kept my eyes fixed on the gate of the backyard.



``Please do keep in touch,'' he said, ``You can come home anytime.''



``Okay,'' I replied.  I wasn't sure if my voice was loud enough for him to hear.



As Lisa led me to her car, I had to steel myself to keep from looking back.





