





Paige's jaw hurt.  Being muzzled like an animal did that.



The other restraints weren't so bad, but that was only in a relative sense.  Her hands were buried in a pair of reinforced metal buckets, each filled with that damn pastel yellow foam.  The buckets themselves were linked together behind her back, with comically oversized chain links.  It would have been intolerably heavy if it weren't for the hook on the back of her chair, which she could hang the chain on.



Strips of metal had been tightened just under her armpits, near the bottom of her ribcage, her upper arms and waist, with two more bands around each of her ankles.  Chains seemed to connect everything to everything else, preventing her from moving her arms or legs more than a few inches in any direction before she felt the frustrating resistance and jangling of the chains.  The heavy metal collar around her neck, thick enough around it could have been a tire for a small vehicle, blinked with a green light just frequently enough that she forgot to anticipate it.  She got distracted and annoyed by its appearance in her peripheral vision each time it flashed.



The irony was, a pair of handcuffs would have sufficed.  She didn't have enhanced strength, no tricks to slip her restraints, and she wasn't about to run anyways.  If any of that was a real possibility, she wouldn't have been allowed in the courtroom.  The prosecution had argued that she \emph{could} have enhanced strength, that she \emph{could} be a flight risk, and her lawyer hadn't done a good enough job of arguing against it, so the restraints had gone on.  Which meant she got trussed up like Hannibal Lecter, as though she were already guilty.  Unable to use her hands, her hair, the vibrant and startling yellow of a lemon, had slipped from where it was tucked behind her ears and strands now hung in front of her face.  She knew it only made her look more deranged, more dangerous, but there wasn't anything she could do about it.



If she had been able to, she would have had a comment or two to make about that, or at least she could have asked the lawyer to tidy her hair.  She would have argued with the man that had been hired as her defense, instead of waiting hours or days for a response to each of her emails.  She would have demanded that her basic rights be met.



But she couldn't say anything.  A leather mask reinforced with the same metal strips that were on her body and a cage-style grille of small metal bars was strapped over her lower face.  The interior of the mask was the worst thing, because the arrangement extended into her mouth, a framework of wires keeping her mouth fixed in a slightly open position, her tongue pressed down hard against the floor of her mouth.  The barbaric setup left her jaw, her tongue and the muscles of her neck radiating tension and pain.



``Silence.  All rise, please.  This court is now in session, the honorable Peter Regan presiding.''



It was so hard to move with the restraints.  Her lawyer gripped the chain running between her armpit and her upper arm, to help her get to a standing position, but she stumbled anyways, bumped into the table.  There was no way to be graceful when you were wearing restraints that weighed half as much as you did.



``Ladies and gentlemen of the jury, have you reached a verdict?''



``We have, your honor.''



Paige watched as the clerk delivered the envelope to the judge.



``In the matter of the state of Massachusetts versus Paige Mcabee, as to the count of attempted murder, how do you find?''



``Not guilty, your honor.''



Paige sagged a little with relief.



``In the matter of the state of Massachusetts versus Paige Mcabee, as to the count of aggravated assault with a parahuman ability, how do you find?''



``Guilty, your honor.''



Paige shook her head as well as she was able.  No!  This wasn't fair!



She almost missed the next line.  ``\ldots{}sexual assault with a parahuman ability, how do you find?''



``Guilty, your honor.''



\emph{Sexual assault}.  The words chilled her.  \emph{It wasn't like that.}



``Is this your verdict?''



``Yes, your honor.''



``Paige Mcabee, please direct your attention  to me,'' the judge spoke.



She did, eyes wide, shellshocked.



``Determining sentencing for this case is not easy.  As your lawyer has no doubt made you aware, you do fall under the umbrella of the TSPA, or the three strikes act.  At the age of twenty three, you have been convicted of no prior crimes.



``According to the witnesses heard in this court, you first demonstrated your abilities in early 2009.  You were vocal about not wanting to become a member of the Protectorate, but you also expressed a disinterest in a life of crime.  This state, in which an individual does not identify as hero or villain, is what the PRT classifies as a `rogue'.



``It is in our interests to promote the existence of rogues, as the proportion of parahumans in our society slowly increases.  Many rogues do not cause confrontations, nor do they seek to intervene in them.  Instead, the majority of these individuals turn their abilities to practical use.  This means less conflict, and this serves the betterment of society.  These sentiments mirror those that you expressed to your family and friends, as we heard in this courtroom over the last few weeks.



``Those facts are in your favor.  Unfortunately, the rest of the facts are not.  Understand, Miss Mcabee, our nation uses incarceration for several reasons.  We aim to remove dangerous individuals from the population and we do it punitively, both for justice against transgressors and to give other criminals pause.



``Each of these applies in your case.  It is not only the heinous nature of the crime that must be addressed by the sentencing, but the fact that it was performed \emph{with a power}.  Laws are still new in the face of parahuman criminality.  We become aware of new powers on a weekly basis, most if not all warranting careful and individual attention in respect to the law.  In many of these cases, there is little to no precedent to fall back on.  As such, the courts are forced to continually adapt, to be proactive and inventive in the face of new circumstances that parahuman abilities introduce.



``It is with all of this in mind that I consider your sentencing.  I must protect the public, not only from you, but from other parahumans that might consider doing as you did.  Placing you in standard detention proves problematic and exorbitantly expensive.  It would be inhumane and harmful to your body to keep you under restraint for the duration of your incarceration.  Special facilities, staff and countermeasures would have to be arranged to keep you in isolation from other inmates.  You pose a significant flight risk.  Finally, the possibility of you re-entering society, by escape or parole, is particularly concerning, given the possibility of a repeat offense.''



``It is with this in mind that I have decided that there is sufficient cause to sentence you outside the scope of the TSPA.  Guilty on two counts, the defendant, Paige Mcabee, is sentenced to indefinite incarceration within the Baumann Parahuman Containment Center.''



The Birdcage.



The noise in the courtroom was deafening.  A roar of cheering and booing, movement, people standing, reporters pushing to be the first ones out the door.  Only Paige seemed to be still.  Cold, frozen in stark horror.



Had she been able, that might have been the moment she lost it.  She would have screamed her innocence, thrown a fit, even swung a few punches.  What did she have to lose?  This sentence was little better than an execution.  Some would say it was worse.  There would be no escape, no appeals, no parole.  She would spend the rest of her life in the company of monsters.  With some of the people that were kept in there, the `monster' description was all too literal.



But she wasn't able.  She was bound and gagged.  Two men that were bigger and stronger than her placed their arms under her armpits, practically carrying her out of the courtroom.  A third person in uniform, a burly woman, walked briskly beside them, preparing a syringe.  Panic gripped her, and with her having no way to express it, do anything with it, the hysteria only compounded itself, making her panic more.  Her thoughts dissolved into a chaotic haze.



Even before the syringe of tranquilizers was jammed into her neck, Paige Mcabee fainted.



\sectionbreak



Paige woke up and enjoyed five seconds of peace before she remembered everything that had happened.  Reality hit her like a splash of cold water in the face, somewhat literally.  She opened her eyes, but found them dry, the world too bright to focus on.  The rest of her was damp, wet.  Beads of water trickled down her face.



She tried to move, and couldn't.  It was as though something heavy had been piled on top of her.  The paralysis terrified her.  Paige had never been able to stand being unable to move.  When she had gone camping as a kid, she had preferred to leave her sleeping bag unzipped and be cold rather than be confined inside it.



It was that foam, she realized.  The restraints weren't enough, they'd sprayed her with the stuff to ensure that everything below her shoulders was covered.  It gave a little to allow her to exhale, she could even shift her arms and legs a fraction, lean in any given direction. The harder she pushed, however, the more resistance there was.  The second she relaxed her efforts, everything sprung back to the same position with the foam's rubbery pull.  She felt nausea well in her gut, her heartbeat quickening.  Her breathing increased, but the mask made even her breath feel confined.  The water made her mask damp, so it clung to her mouth and nose.  There were slits for her nostrils and mouth, but it was so little.  She could not take a deep breath without drawing water into her mouth, and with her tongue depressed, she could not swallow easily.



The room lurched, and she had to stop herself before she lost her breakfast.  Puking with the mask on, she might choke.  Dimly, she realized where she was.  A vehicle.  A truck.  It had passed over a pothole.



She knew where it was taking her.  But if she couldn't get free, she was going to lose her mind before she got there.



``The little bird's awake,'' a girl spoke, with a hint of a nasal Boston accent.



``Mmm.''  A man grunted.



Paige knew the `bird' reference was due to the stray feathers that stuck out of her scalp.  Her powers had come with some extremely minor cosmetic changes, turning her hair the bright yellow of a banana or baby duck.  It affected all the hair on her body, even her eyelashes, eyebrows, the fine hairs on her arms.  The feathers had started growing in a year ago, the exact same shade as her hair, only a handful at a time.  At first, alarmed and embarrassed, she'd clipped them off.  Once she'd realized that no further changes were occurring, she'd relaxed and let them grow in, even showed them off.



Paige turned her attention to the two people in the vehicle with her, glad for the distraction from her burgeoning panic.  She had to force her eyes to stay open, painful as the light was, wait for her eyes to focus.  Sitting on the bench beside her was a girl about her own age.  The girl had an Asian cast to her features.  Her eyes, though, were a very pale blue, betraying some Western heritage.  The girl wore the same orange jumpsuit as Paige, and every part of her except her shoulders and head were covered in the yellow-white foam.  Her straight black hair was plastered to her scalp by the wet.



The man sat on the other bench.  There was more foam around him than there was around Paige and the other girl combined.  Topping it off, a cage of metal bars surrounded the foam, reinforcing the setup.  The man was Asian as well, no less than six feet tall.  Tattoos swept up the sides of his neck and behind his ears, into the midst of his wet black hair; Red and green flames, and the head of what could have been a lizard or dragon, drawn in an Eastern style.  He was glowering, his eyes hidden in shadows, oblivious to the endless spray of mist that sprinklers in the truck's roof were generating.



``Hey, little birdy,'' the girl sitting across from Paige spoke.  She was staring at Paige as if those cold eyes of hers could look right through her.  ``Here's what we're going to do.  You lean to your right as hard as you can, then shove yourself left on my signal.  But you keep facing the back door there, alright?''



Paige glanced to her right.  The back door of the truck looked like a vault door.  She quickly glanced back at the Asian girl.  Did she really want to turn her back to this person?



The girl seemed to note Paige's hesitation.  She lowered her voice to a hiss that made Paige's skin crawl.  ``Do it.  Unless you really want to gamble on the chance that I'd be able to find you in the prison, if you don't do as I say?''



Paige's eyes widened.  \emph{This} was the sort of person she was going to be locked up with.  She shook her head.



``Good, little birdy.  Now lean to your right, look at the door.''



Paige did, straining her body to move as close to the door as she could.



``And back!''



She heaved herself the other way, eyes still on the door.  Something heavy cracked against the back of her head.  She tried to pull away, sit upright again, but was stopped as the mask caught on something.



When she felt hot breath on the back of her neck, she knew what she'd caught on.  The other girl had gripped the strap of the mask in her teeth.  There was a tug, then the girl lost her grip, and the two of them were pulled back to their individual positions by the rubbery foam.



``Shit,'' the girl growled, ``Again.''



It took two more attempts.  On the first, the strap came free of the buckle.  On the second, the girl gripped the mask itself and pulled.  Paige turned her head in the girl's direction so the pacifier-cage on the inside of her mouth could be pulled free.



Tendrils of drool extended down from her mouth as she worked her jaw and tongue, trying to swallow properly.  She let out a little whimper as sensation returned to the parts of her face that had gone numb.



``Two qweshionsh,'' the Asian girl mumbled, her teeth still gripping the mask's leather between them, ``Youh poweh?''



Paige had to work her jaw and mouth a second before she could speak, ``My power?  I sing.  Really well.''



The Asian girl frowned, ``Whaf elth?''



``I\ldots it makes people feel good.  When I get going, I can affect them, alter their emotions, make them susceptible to following instructions.''



The girl nodded, ``Teh collah?''



Paige looked down at the heavy metal collar around her neck, ``It's set up to inject tranquilizers into my neck if I sing or raise my voice.''



``Okah,'' the girl mumbled, ``Take teh mahc.''



``Why?''



``Take ih!''



Paige nodded.  They leaned away from each other, then swung together, the girl passing the mask to her.  She clenched it in her teeth, feeling her jaw ache.



``Drop that and I'll \emph{turn you inside out},'' the girl spoke, ``Lung.  Hey, Lung?  Wake up.''



The man sitting opposite them raised his head a fraction, opened his eyes.  Maybe.  Paige couldn't quite tell.



``I know it's hard with the stuff they pumped into you, but I need your power.  Birdy, lean forward, show him the mask.''



Paige did her best to push herself forward against the foam that was layered against her chest and stomach, gripping the strap in her teeth, the mask dangling below her chin.



``I need you to heat the metal, Lung,'' the girl spoke.  ``Get it fucking hot.''



Lung shook his head.  When he spoke, there was no Boston accent in his voice.  The accent that was there made his words clipped, clearly not the voice of a native English speaker.  ``The water.  Is too wet, too cold.  And I cannot see it well.  My eyes have not healed entirely, and it is hard to see through this spray.  Do not bother me with this.''



``\emph{Try}, you miserable fucker.  Failure of a leader.  It's the least you can do, after getting your ass kicked by a little girl, \emph{twice}.''



``Enough, Bakuda.'' he growled.  He slammed his head back against the metal of the truck's wall behind him, as if to punctuate his statement.



``What?  I couldn't hear that,'' the girl, Bakuda, grinned with a hint of mania to her expression, ``Your voice is too fucking high pitched for my range of hearing!  You pathetic\ldots halfbreed\ldots eunuch!''



``Enough!'' he roared, again slamming his head against the wall of the truck.  ``I will kill you, Bakuda, for these insults!  I will tear your arm from your socket and I will shove it-``



``Pissed off?!'' she interrupted him, practically screeching, ``Good!  Use it!  Heat the motherfucking metal.  The metal strip around the edges!''



Still panting with the exertion of shouting, Lung turned his attention to the mask.  Paige winced at the blast of heat against her face, started to pull away, but stopped as Bakuda spoke.



``Focus it!'' Bakuda shouted, ``Focus on the edges!''



The radiation of heat ceased, but Paige became aware of a stringent, smoky smell.



``Hotter!  As hot as you can get it!''



The smell was too strong, too acrid.  Paige coughed a few times, hard, but she didn't lose her grip on the mask.



``Now, birdy!  Same maneuver as before, but don't let go!''



Paige nodded.  She leaned away, then swung in Bakuda's direction.  What followed surprised her more than when Bakuda had bitten into the strap of the mask.



The Asian girl set about savaging the red hot metal with her teeth, digging into it even as they had to pull away.  Softer with the heat, the thin metal strip pulled free of the mask itself.  The metal that ran along the strap cut Paige's lip as it came off.  She almost -almost- dropped the mask, but managed to snap her teeth to catch the buckle in her teeth before it could fall to the floor.



As the strip came free, Bakuda pulled back and jerked her head to one side, hard, impaling herself in the shoulder with one end of it.  She screamed, and blood ran from one of the burns on her mouth.



Paige looked at Lung.  The huge man did nothing, remaining silent.  He only watched dispassionately as Bakuda's chest heaved with the exertion and pain, her head hanging down.



``What the hell are you doing?'' Paige breathed.



``No hands, have to make do,'' Bakuda panted, ``Again.  Before my body realizes how badly I'm hurting it.''



Paige nodded.  She wasn't about to argue with the supervillain that was threatening to turn her inside out.



The ensuing attempts weren't any prettier or easier.  The second long metal strip was freed and Bakuda impaled that one in her shoulder as well.  The metal grilles from the exterior and interior parts of the mask were next to be pulled free.  Paige was left holding only the leather portion of the mask, the straps and the covering that had gone over her mouth and nose.  Seeing Bakuda gingerly balance the metal grilles on her free shoulder, against the tacky foam so they wouldn't slip down, Paige did the same with the leather of the mask.



``What did you do to get sent here?'' Paige asked.



``Last I heard, before we lost power to our neighborhood, the body count was almost at fifty.''



``You killed fifty people?''



Bakuda grinned, and it wasn't pretty, with her lips as ravaged as they were.  ``Injured more, too.  And there were those who got brain damage, one or two might've gone homicidally insane, and I know a bunch got frozen in time for a hundred years or so\ldots it gets blurry.  Crowning moment was the bomb.''



``Bomb?'' Paige asked, eyes widening.



``Bomb.  They said it was as powerful as an atom bomb.  Idiots.  They didn't even understand the technology behind it.  Philistines.  Sure, it was about that powerful, but that wasn't even the real damage.  Amazing thing would've been the electromagnetic wave it generated.  Wipe every hard drive, fry every circuit board for every piece of machinery over a full \emph{fifth} of America.  The effects of that?  Would've been worse than any atom bomb.''



Unable to even wrap her mind around that, Paige glanced at Lung.  ``And him?''



``Lung?  He's the one who told me to do it.  Man in charge, he is.''



Lung's head moved fractionally, but with the shadows under his brow, Paige couldn't tell if he was watching.



``You?''  Bakuda asked Paige. ``What'd you do to get sent here?''



``I told my ex to go fuck himself.''



There was a pause, then Bakuda started cackling.  ``What?''



``It's complicated,'' Paige looked away and down.



``You gotta explain, birdy.''



``My name's Paige.  My stage name was Canary.''



``Ooooh,'' Bakuda spoke, still cackling a little as she gripped one of the metal strips that was spearing her shoulder and pulled it free.  Holding it in her teeth, she spoke, ``That'sh no good.  You calling yourshelf Canary in \emph{prishon}?''



``I didn't intend on going to prison.''



``Who doesh?''



``I mean, I'm not even a supervillain.  My power, it makes me a fantastic singer.  I was making a lot of money doing it, there was talk of record deals, we were moving to larger venues and my shows were still selling out\ldots everything was perfect.''



Bakuda let the strip swing from her teeth until it dangled, then carefully maneuvered it until she was gripping the far left side of it.  She leaned back, her head facing the ceiling, as she slid the other metal strip, the one impaled in her shoulder, into her mouth as well, so she was holding one end of each strip in her mouth.  Pausing, she asked, ``Whaf haffen?''



Paige shook her head.  It was the testimony she'd never been able to speak out loud, at her trial.  ``I'd just finished my biggest show yet.  Two hours on stage, a huge hit, crowd loved it all.  I wrapped up and went backstage to rest, get a drink, and ran into my ex.  He told me that since he was the one who pushed me to get out on stage in the first place, he deserved credit.  Wanted half the money.''  She laughed a little, ``Ridiculous.  Like I'm supposed to ignore the fact that he cheated on me and told me I was never going to make it for real when he left.''



Bakuda nodded.  She pulled away from the strips, where she'd managed to tie them in the semblance of a knot.  She used her teeth to bend the now-joined strips into an L-shape.  With the end that wasn't impaled in her shoulder now in a position in front of her, she closed her mouth on it.



``We argued.  Then I told him to go fuck himself.  He left, and I didn't give it a second thought\ldots until the police showed up at my door.''



Bakuda pulled her mouth away from the end of the strip.  She'd bent it into a loose `v' shape.  She frowned at it, then glanced at Paige, ``And?''



``And he'd done it.  I- I guess I was still amped up from my performance, and my power's effects were still empowering my voice, or he was in the audience and was pretty heavily affected.  So when I told him to go fuck himself, he, um, he did.  Or he tried, and when he found it wasn't physically possible, he hurt himself until\ldots''  Paige closed her eyes for a moment.  ``Um.  I won't go into the details.''



``Mmmm, shucks to be im.  Oo `oo'' Bakuda raised her eyebrows, still working the metal strip inside her mouth.  She pulled away, verified the end as being in a rough `o' shape, and then gripped the strips in her teeth to pull the entire thing out of her shoulder with a grunt.  She placed the end she'd just reworked against the bench and slid her mouth down the length of the metal, so she could get a grip on the other end.



Taking hold of it in her teeth, she turned her attention to the wall of the truck between herself and Paige.  There were locks placed at regular intervals against the wall, meant to secure the chain of standard handcuffs in place, for those not doused in foam.  She began feeding the metal strap through the loop of the lock.  Beads of sweat mingled with the water running down her face as she worked.



The knot joining the two straps jammed in the hole.  Bakuda pushed a little harder, and wedged it firmly in place.  The L-bend in the metal placed the closed `o'-shaped loop of metal close to Paige's shoulder.



``Any bets on Oni showing up?'' Bakuda asked Lung.



``I would be surprised,'' he rumbled his response.



She gripped one of the metal grilles in her mouth and began working at it with her teeth.  It was all one thin piece of metal, bent and woven like chain link fencing, albeit a tighter mesh.  Now that it was no longer held securely in place by the metal strips, Bakuda was free to start unwinding and straightening it.



When it was almost completely unwound, she adjusted her bite on it and clenched the second mass of wire, the one that had been in Paige's mouth, in her jaws, bunching it together into a cylindrical mess about four inches long and one inch across.  Still biting it, she turned her head so the mostly straight four-foot length of wire was pointing at Lung, not two feet away from his face.  Her mouth still around the tangle of wire, she mumbled, ``Need end hot.''



Lung growled, but he did as he was asked.  When the end was white hot, Bakuda quickly adjusted her grip, letting go and biting again until the tip was near her mouth.  Lips pulled back, she bit down on it.



``How can you do that?'' Paige asked, ``Doesn't it hurt?''



``No uffing hit ih urhs,'' Bakuda growled.  She pulled away, set it so the handle was against the bench, the length of wire against her shoulder, and examined her handiwork.  ``But tooth enamel is tougher than you'd think.''  She spat a measure of blood out onto the floor of the truck, then bit down twice more, pausing between bites to turn the length of metal with her teeth, lips and tongue.



When she extended the length of wire in Paige's direction, sliding it through the `o' shaped end of the metal strip, Paige realized what Bakuda had spent this much time setting up.  She didn't even need to be asked to bend down against the foam restraints and crane her neck to one side, to put her collar in reach of the overlong makeshift screwdriver.   The metal strip with the loop in the end served to hold the portion closest to Paige up, so Bakuda could direct it more easily.



It wasn't fast work.  Bakuda had to use her teeth, jaw and a turning of her head to rotate the screwdriver, and it was a chore to get it back in position if she lost her grip on it.  Ten long minutes of silence and grunting were broken only by the sound of two screws dropping to the metal bench, before Bakuda stopped to take a rest and ease her jaw.



``You won't be able to do anything to my collar without setting it off,'' Paige spoke.



``Dumb bitch,'' Bakuda muttered, sticking out her lower lip and peering down as if she could investigate the degree of damage to her own lips.  ``I'm a bomb expert.  I understand triggers and catalysts on the same fundamental level you understand walking and breathing.  I can visualize mechanical things in a way you couldn't with five college degrees and a hundred years.  Insult me like that again and I'll \emph{end} you.''



As if pushed to prove herself, she gripped the screwdriver in her teeth again, and set to work again.  A panel was pried off, and the unscrewing was resumed, deeper in the collar.



Paige hesitated to talk again, knowing how easy the girl was to provoke, but the silence was crushing.  ``I guess it's a good thing this is a long drive, from Boston to British Columbia.''



``You were asleep a while,'' Bakuda pulled away from the screwdriver, talking softly, as if to herself.  ``Not as long as you think.''



Paige felt something come free from the heavy collar around her neck, saw Bakuda tilt the screwdriver upward, sliding a glass tube with something glowing inside down the length of the metal bar  After another few minutes, another piece of machinery joined the glass tube, as though it were a high-tech shish-kabob.



``Tragic,'' Bakuda spoke, on her next rest.  ``This is beautiful work.  Not the actual assembly, that's crap.  It's obvious the tinker that designed this intended it to be put together by regular schmoes.  Wouldn't have screws and shit, otherwise.  But the way it's designed, the way everything fits together\ldots makes a scientist proud.  Hate to butcher it.''



Paige nodded.  She didn't know enough about that sort of thing to risk commenting.  As scary as this situation was, as curious as she was, she felt the lingering effect of tranquilizer in her system, an impending boredom.



She closed her eyes.



It didn't feel like her eyes were closed for more than a minute before she was woken by a shout of ``Birdy!''  Paige jolted awake, turned to Bakuda, and saw the work was done.  Bakuda hadn't just disabled the collar, but had assembled components into a roughly sphere-shaped setup of metal and wires.  It dangled from the remains of the mask and strap, which Bakuda held in her teeth.



Lung spoke, his voice low, slightly accented, ``We have stopped.  Her device will buy us time, and you will use it to sing.  The bomb will not do much damage, but it will slow them and dose anyone hit with a small amount of sedatives.  This will make it easier for you to control them, Bakuda says.  You will then get them to free us.''



Paige's eyes went wide.  She nodded.



There was a loud sound outside the truck, and Bakuda started swinging the device left and right like a pendulum.  The metal doors at the back of the truck slammed open, and Bakuda let go.  The device rolled out the door.



Paige sang, not stopping as the device detonated, rocking the truck.  Her song was wordless.  She was her own accompaniment, using the acoustics of the truck's interior to generate echoes.  She charged her voice with her power, willing those who heard it to obey, to submit in a way she'd never done before.



It might have worked, if there was anyone around to hear it.



A giant metal claw entered the back of the truck, closed around Lung, and dragged him out.  When the claw returned to claim her, she stopped singing, started shrieking instead.



``No!'' Bakuda's screams joined her own, behind her, ``Fuck you!  No!  No!  I had a fucking plan!''



The arms moved along slats in the ceiling, carrying them through what looked like a massive underground bunker.  Everything was concrete, and the room was so vast that Paige could not even see any of the walls.  There was only the ceiling twenty or thirty feet above them and the floor, extending endlessly around them, lit by fluorescent lights at regular intervals.  The only thing breaking up the empty expanse was the armored truck bearing the PRT identification on the side and a black square attached to the ceiling, further down.



The arms arranged them in front of the black square – an oversized monitor.  A face, clearly a CGI rendering intended to mask the real identity of the speaker, appeared on the screen.  When the voice came from the speakers, the filter intended to disguise the woman's voice didn't quite hide her strong accent.  Paige tried to place it.  Not Southerner, not Cockney, but maybe similar?  She'd heard someone with that accent before.



``Prisoner 599, codename Lung.  PRT powers designation Brute 4-9 asterisk, Blaster 2-6 asterisk, fire and heat only.  Individuals reading or viewing this log are directed to see page three and four of prisoner's file for particulars on powers.  Recommended protocols were properly carried out with sprinkler system and added restraints.  Chance of escape following interment in the Baumann Parahuman Containment Center rests at a fairly steady .000041\% with no gross deviations in any likely scenarios.  Within acceptable limits.  Will be processed to cell block W.''



``You're Dragon,'' Bakuda spoke, eyes widening, ``No shit.  Best tinker in the fucking world.  I'd say I'm a fan, but I'd be lying.''



Paige couldn't help but react to that as well.  Dragon had designed the Birdcage and much of the gear the PRT used, including the containment foam.  She was head and shoulders above any of the other tinkers that went out in power armor.  Dragon sported a wildly different suit each time she deployed.  Her stuff was so advanced that a group of criminals who had gotten away with stealing a damaged suit of her armor were now using that same technology to operate as top of the line mercenaries – the Dragonslayers.



Dragon was also Canadian, which was the detail Paige needed to peg her accent as that of a Newfoundlander.  Not an accent one heard very often, these days.



``Prisoner 600, codename Bakuda.  PRT powers designation Tinker 6 with bomb speciality.  Recommended protocols were \emph{not} properly carried out.''  The formal tone of the voice dropped away as she muttered, ``I hate to get someone fired, but I'm going to have to report this.  Supposed to be in an S-class containment truck and placed no less than six feet from other prisoners\ldots well, at least nothing came of it.''



``Fuck you, Dragon,'' Bakuda snarled.



``\ldots{}Chance of escape from the Baumann Parahuman Containment Center is .000126\% with potential gross deviation in the event of introduction of contraband material or a matter producer.  With monitoring this chance drops to .000061\%.  Will be processed to cell block C.''



``Prisoner 601, codename Canary.  PRT powers designation Master 8.  Recommended protocols were properly carried out, with provided restraints and no human personnel being brought within three hundred yards of said individual's position.  Hi Canary.''



Paige blinked a few times in surprise, ``Hi?''



``I followed your trial.  I thought it was a damn shame things went like they did.  I get that it was a reckless accident, but you don't deserve to be \emph{here}.  I even wrote a letter to your judge, the DA and your governor saying as much.  I'm sorry it wasn't enough.''



The sympathy hit Paige hard.  It was all she could do to stop herself from bursting into tears.



``I'm afraid I've got to do my job, and that means carrying out my role in enforcing the law.  You understand?  Whatever my feelings, I can't let you go.''



``I- Yes.''



``Listen, I'm sticking you in cell block E.  The woman that put herself in charge of that cell block goes by the codename Lustrum.  She's a pretty extreme feminist and misandrist, but she protects the girls in her block, and it's also the block furthest from the hole the men opened into the women's half of the Birdcage.  If you're willing to play along, buy in or pretend to buy into her way of thinking, I think she'll keep you safest.''



Paige didn't have words to reply.  She just nodded.



``Ok.  Prisoner 601's Chance of escape from the Baumann Parahuman Containment Center is .000025\% with no gross deviations.  Do you three understand why I'm telling you this?''



``Our chances of escaping are pretty slim,'' Bakuda spoke.



``Yes.  The Baumann Detention Center is a structure so complex I had to design an artificial intelligence to put it together.  It's situated inside of a hollowed out mountain, the walls of which are lined with layers of a ceramic of my own design, each such layer separated by volumes of dormant containment foam.  If you punched a hole in the outside of the mountain, you'd only wind up with more foam than you knew how to handle.



``That's the \emph{mountain}.  The prison itself is nicknamed the Birdcage because it is \emph{suspended} in the center of the empty mountain, hanging only by the same network of tubes that supplies prisoners and food to the cell blocks.  Both the interior of the tubes and the interior of the mountain itself are vacuums.  Even if an individual were to have powers allowing them to navigate the vacuum, I have three thousand antigrav drones in position at any given time, laying dormant in that lightless void, waiting for any signal, motion, energy or air leakage to awaken them.  Once awakened, a drone will move to the location of said anomaly and detonate.  Many of my drones contain a loadout of containment foam, but others contain payloads designed to counteract various methods one could theoretically use to traverse the vacuum.  Some are quite lethal.''



``These are not the only measures I have taken, but it wouldn't do to inform you of everything I have done to secure this facility.  Know only that your chance of successful escape is negligible, and the chance of you dying or being maimed for attempting it is much higher.''



``Know that while I do retain control over the structure and the ability to observe those within, enabling me to respond to emergencies such as natural disasters, you will not be able to manipulate this to your advantage.  I will not, \emph{cannot} intervene should a hostage be taken, or if an individual should threaten or perform damage to vital or luxury resources.  There was no other way to run the prison effectively than to have you police and protect yourselves.  I stress: nothing you do can convince me to free you.  The elevators to the Baumann Detention Center go one way.  Down.''



``I will be depositing you in the elevators now.  You will be provided with a limited measure of oxygen, sufficient only to carry you safely to the bottom.  Should you slow or stop the lift, or attempt to scale the interior of the tube, I expect you will likely fall unconscious, suffer brain damage or die for your trouble.  A counteragent for the containment foam will be applied as you descend, so that you are free before you reach the bottom.''



Lung and Bakuda were carried off in different directions.  Paige was the last to be carried away by the robotic arms.



``I am sorry, Paige Mcabee,'' Dragon's tinny voice sounded, as the arm set her down.  ``Good luck.''



The ground beneath her shifted, and then she descended.



\sectionbreak



Lung walked with confidence to the `hole', a word with double meaning, as it referred to the actual hole in the wall, as well as the more vulgar term for why many in the men's half of the Birdcage went there – it was the sole route into the women's prison.



A group of women were on guard on the other side of the hole, standing or sitting at various vantage points there.



``Who're you?'' one of the women asked him.  She was a striking woman with coffee colored skin and a mouthful of teeth that looked like knife blades.



``I am Lung.''



``You're new?''



``Yes.''



``Which cell block are you in?'' this question came from a heavyset woman that looked more like a middle aged soccer mom than a prisoner.  Lung noted, however, how each of the other girls that were on guard turned to listen when she spoke.



``W, ma'am,'' he spoke, taking extra care to not offend.



``You want a girl?''



``I am here only to visit one of my subordinates.  Cell block C.''



``Even if you aren't buying, can't let you through for free.  Gotta pay something.  Marquis runs your cell block, still?  Divvies up the cancer sticks from his food crates fairly enough?''



``Yes.''  Lung reached into his pocket and retrieved a half-carton of cigarettes.  He handed them over.



``Good boy.  Listen, Glaistig Uaine runs the cell block you're going to.  You keep some of these sticks, you give them to her, so as not to insult her.''



``I will.  Thank you for this advice.''



``I do like a polite boy.  You run along, now.''



He bowed his head in respect, then walked briskly to the next cell block.  A smaller contingent of guards awaited him there, and he handed over the remaining cigarettes, specifying them as a gift for Glaistig Uaine.  The guards parted to let him through.



He found Bakuda in a cell all to herself.  The walls of the prison were all metal of some sort, painted a dark blue, but Bakuda had scratched formulas and sentences into the walls of her cell, where they glittered silver-gray in the right light.  Her cot was pulled into the center of the room to give her more surface to write on.



``Bakuda,'' he spoke.



``Lung!  This place is amazing!'' she grinned maniacally, her scarred lips spread wide, ``I thought it would suck, but it's\ldots it's like being inside the fucking Mona Lisa of architecture.  Genius shit.  She wasn't lying about this place being inside a vacuum, but what's amazing is what happens when you breach the outside.  See, she didn't make this place tough.  It's \emph{fragile}.  Like she built the most complex house of cards ever.  You knock a hole in the wall, and you're not only pretty much guaranteed to off yourself, but the change in air pressure changes the room configuration, seals off the space so the breach doesn't affect anyone in other rooms.  And even if you stop the main bits from sliding down, the drop in air pressure carries into the next room, and \emph{that} room seals off.  I could spend a decade figuring out how she did this.  And that's the simplest part of it.  In busier areas-``



``I do not care about this,'' Lung interrupted her breathless rambling.



Bakuda stopped and wheeled around, still grinning.  ``Ok.  How you doing?''



``Satisfactory.  My eyes are healing, but I am still having trouble seeing color.  I do not like the leader of my cell block, but he is a fair man.  He has given me his favor in exchange for telling him about Brockton Bay, a place he once operated.  This has helped ensure I am not bothered.  That, and the prisoners seem to wait to see what each new inmate can do before they pick him as a target.''



``Yep.  It looked pretty grim for me for a few days, but when the freaky girl in charge of this block found out I could fix the televisions here, things suddenly got a lot easier.''



``I see.''



She raised an eyebrow, smiling.  ``So.  Why the visit?  Feeling lonely?''



``No.''



She dropped the smile in the blink of an eye.  ``Then explain.''



``This is your first time in a prison, yes?''



``Yep.''



``I was in prison before I came to America.  There are four ways one can survive in such a place.  You can join one of the gangs or groups in charge.  This was not possible for me then, for I was known to be half Japanese, half Chinese, and there was no gang willing to include such a person.  It is not a possibility for me now, either, for I am too used to being in charge to bow and scrape for any length of time without losing my patience.  It is the route I see you have taken here.''



``Sure,'' Bakuda eyed him warily.



``The second option is to be somebody's bitch.  They give you their protection in exchange for the most base of services.  You understand why I would not take this route.''



``I get it, yeah.''



``The remaining options are to either kill someone or to be seen as a madman.  In such cases, one demonstrates he is too dangerous or unpredictable to be fucked with.''



``So what are you doing?''



``I thought I would choose the third and fourth.''



Bakuda's eyes went wide.  She backed away, then realized the futility of the move.  Lung stood in the middle of the one doorway that led out of the cell.  ``Why?''



``You insulted me.  You failed me.  Because I must kill \emph{someone}, and killing a subordinate of mine who others have cause to protect should also mark me as sufficiently unpredictable.  Others will fear me after this.''



``I\ldots I insulted you to get your power going, you know?'' she squeaked, ``I did it to help our escape.''



``I might have overlooked it for this reason, but we did not escape. You \emph{failed me}, both here and in the city.''



She flicked her arm, and an arrangement of bedsprings and twisted scrap metal dropped from her sleeve into her open hand.  ``I'll punch a hole in the outside of the cell if you come any closer.  Air flows out of the room, door seals shut, we both suffocate.''



``You are not fast enough.''



``Wanna bet?''



He did.





