





I stepped out of the shower, but I didn't dry off.  It was hot out, and the cold beads of moisture on my skin offered something of a reprieve.  I felt acutely aware of the breeze blowing into the room, as it traced frigid lines against my body.  My hair was wet, plastered to my neck, shoulders and back, and water ran down from the individual locks of hair in thin streams.



More than anything, the cool sensation of the wet hair on my head was a contrast to the workings inside my skull.  It wasn't even seven in the morning, and in purely mental terms, I was hitting the ground running.  Had to.



I leaned over the sink, letting the droplets fall from my eyelashes and run down my face.



I reached out, and my toothbrush found its way to my hand, as much as my hand found it.  The toothpaste was much the same, maneuvered to my hand by a dozen threads and twice that many insects.  I took two minutes brushing, another minute to use some mouthwash, and then stood straight, stretching.  My skin felt tight, contracted by the temperature.



Like the act of rubbing one's stomach while patting their head, I was moving out of sync.  I held out one hand for the hairbrush, closed my fingers around it, then set to tugging the plastic bristles through the tangles and knots, slow, strong, deliberate movements, a patient, calming exercise.



My mind?  I was watching, studying, sensing and experiencing ten thousand things at once, an engine going full-bore.  I could follow my dad as he moved through the house, picked work clothes out of his closet, threw away a sock and its matching pair.  I watched every entryway into the house, the windows and doors, tracked the movements of the neighbors, and our neighbor's neighbors.  With fleas, I could track the movements of the neighbor's outdoor cat, a surprisingly violent creature with a sizable body count of local frogs and mice, many killed purely for sport.



I could track each of these details for roughly a thousand feet around me, to the point that I was aware of every person and every piece of terrain in the area.  There were bugs crawling inside walls and the dark corners of houses all up and down the street, and I had only to pay attention for a moment to grasp the layout of each house and home.  I could feel the worms crawling through the earth, the ants navigating the surface, struggling but surviving in the humid heat of the outdoors.  I could feel the maggots that were devouring one of the cat's abandoned victims, the ants working to collect the food before descending into their labyrinthine hive.



And I thought of my own hive, of jobs that needed doing and positions that needed filling, of threats and threat assessment.  I was prioritizing, knowing it would be impossible to do every job in the time I had.  I had to check in with everyone, to look after the individual groups, get more information on construction and finances, to make sure everything was running smoothly.  Each and every task could potentially be interrupted at a moment's notice, so I had to ensure I had people at hand that I could delegate to in a pinch.



It was a lot to take in, a jumble of half-formed thoughts that I only considered for moments at a time before categorizing them, making or postponing a decision.  There were too many I wouldn't be able to address yet.  Tasks that I needed eyes on, people I needed to talk to for information.



I toweled my hair dry, brushed it again, had the bugs clean up the silk strands that littered the bathroom, and then wrapped a towel around myself to venture to my bedroom and get dressed.



By the time my dad descended to the ground floor, I was already halfway done preparing breakfast, standing by the stove with my damp hair tied back into a loose ponytail, wearing a strapless top and loose-fitting, lightweight cargo pants.



Preparing breakfast was another of those routine activities, rubbing my stomach.  I was still patting my head, thinking of how to address one sensitive issue.  When my dad entered the scene, though, I made a deliberate attempt to break from that mode of thinking, to shift mental gears.



``You're going to school wearing that?'' my dad asked.



``I'm going running like this,'' I replied.



``In this heat?  Take some water with you.''



I pointed at the kitchen table, where I'd set two water bottles by the salt and pepper shakers.



``Good.''



``Crepe?'' I asked.  ``And fruit salad?  We have some left over from last night.''



``Please.''



I slid the crepe out of the frying pan and onto a plate, then handed it to him.  I dropped some butter on the pan, poured more batter on, and then tilted it until the batter was spread thin over the surface.



``You're usually out the door by now, and back fairly late.''



``Trying to do my part,'' I said.  ``And I wanted to talk.''



``Okay.  I like talking,'' he said.  ``Unless this isn't the kind of conversation we look forward to?''



He made a face as he eased himself down into his chair.  \emph{ He's still not completely recovered}.  I admitted, ``It isn't.''



``Ah,'' he said.  His expression was placid, his eyes watching me carefully.



``I was thinking\ldots I don't think I'll go back to school.''  I turned my eyes to the crepe.  I poked the spatula at the corner to verify it was more solid, lifted it, then flipped the thing over.



I could hear him pouring orange juice.  Flies hidden on ledges and on a shelf between cookbooks could see the vague movement as he raised the glass to his lips and drank before he spoke.  ``It's a month and a half of classes.  Everyone will be catching up, not just you.  We couldn't ask for better circumstances.  A new environment, new people, a new dynamic.  \emph{You're} different.''



``I am,'' I said.  I slid the crepe onto a plate.  I didn't use the fruit salad, but instead went straight for the blueberries I'd defrosted, adding a spoonful of cream.  I rolled it up, spooned some fruit salad onto the side of the plate, collected my mug of tea by the side of the stove and then sat down opposite my dad.



He looked so \emph{old}.  Two serious sets of injuries, one he hadn't fully recovered from, and a measure of stress that I was partially responsible for, all adding up to artificial years.  I felt a pang of fondness mixed with regret.



``If I asked you to, would you?'' he asked.  ``Hypothetically.''



``If you did, I would,'' I admitted.  ``But it's not where I want to be right now.''



He nodded, taking a bite.  A dribble of fruit juice ran down from the corner of his mouth, and he thumbed it away.  I reached for a roll of paper towels, tore one off and handed it to him.



``Thank you,'' he said.  It wasn't a response to my statement.



If he asked, I'd find a way.  Work things out.  Reprioritize, filter out the nonessential tasks, shift things around.  Everything would take longer, there would be issues in countless areas, more things I couldn't do and people I couldn't protect.  But I'd do it.



``What will you do instead?''



``What I've been doing.  I'll work,'' I said.  ``There's cleanup work, still.  It pays pretty well, all things considered.''



``It's not easy,'' he said.



``I'm tough,'' I said, flexing an arm.  I had some muscle, but it looked pretty sad on my thin arm.  I let my arm drop.  ``At least it's not all heavy lifting.''



``But it wears you out.  I won't say it's \emph{bad} work, we both know how many hundreds of people I've worked with who are employed along those lines.  \emph{I've} been employed along those lines.  But you're smart.  Your mom and I both expected you to go on to college.  The idea that you might never graduate high school never crossed our minds.''



\emph{Bringing Mom into it}.  I sighed.  ``I will graduate.  I promise.  But I can wait a year, study online.''



``Why?  Why put things off and study for half a year to a year, when you could pass tenth grade in two months?''  He didn't sound angry or upset, only confused.



\emph{Prioritizing, weighing every action against the costs involved}.  \emph{Spending most of my day at school, everything else takes a back seat.}



``Like you said, I'm different than the person I was,'' I replied.



He looked up at me, met my eyes, and I could feel my blood run cold.  That searching, studying look\ldots



\emph{He knows?}



``You are,'' he said, simply.  Not a confirmation of my fears, not dismissing them either.  It was only an admission of what we both knew as truth.



``If you want me to go, you can tell me to go.  I will.  You're my dad.  You can tell me to do something, and I have to do it.''



``No,'' he said, shaking his head.  ``We both know that's not true.''



I took another bite of my crepe instead of replying.



``Being a parent, there's always that niggling fear, that notion that maybe one day your child will realize you're not all-knowing, not all-powerful.  That they don't really \emph{have} to do anything you say.  But you spend years growing up together, parent and child, as a parent you get accustomed to acting like you're in power, believing it as much as your daughter does.  For some, for \emph{most}, that confidence gets worn down after the child hits adolescence, and the parent changes from being one of the most important figures in their child's life to being an embarrassment.''



``You were never embarrassing to me,'' I said.



``I know,'' he said.  ``But that makes it harder, doesn't it?  For all those other parents, it's a transition, a transformation, as their children gradually test their authority and discover how very fragile a thing it is.  For me?  I didn't have nearly enough time to get used to it.  One night, one conversation, and you decided I didn't have any say in your life anymore.''



``You do,'' I said, feeling alarmed, in a way I couldn't articulate.  ``I \emph{want} you to have a say.  I'm saying you can set curfews or demand that I go to school, and I \emph{will}.  I might complain or argue, but I'll listen.  I'll \emph{let} you have a say.''



He reached across the kitchen table, taking my hand.  He pulled it towards him, and I let him stretch my arm out straight.  He bent over and kissed the fingers.



His voice was quiet, ``I hope that, if and when you ever have a child of your own, you never have to hear them say anything like that.''



He released my hand, and I withdrew it.



``You're sure you don't want to go to school?''  He asked.



I nodded.



``It's your decision,'' he said.  ``Yours, not mine.  Where would you work?''



``The Boardwalk,'' I said.  ``It's close, it's good pay, good food, and it's safe.''



``A little more directly involved with the local supervillain-in-power than I'd recommend for  any employees of mine that were looking for a job,'' my dad replied.



I didn't have a response to that.  I ate the last bite of my crepe.



``Will you still be there at lunchtime?''



I nodded.



``I'll meet you.  Things are busy, things are \emph{good}, but I'd like to set aside a block of time.  We can pick up lunch, or I'll bring something.  How's that?''



It was awkward on a dozen different levels.  Even staying here caused me any number of problems.  It removed me from a place I needed to be, it made for awkward transitions between my civilian and costumed life, and every conversation with my father stressed me out, left me wondering if he could guess.  Or maybe when I stepped in the door, I might find out that the local heroes had recognized me, using one of the mutant clones that had been running around, or any number of other possibilities.  My dad waiting to ambush me with the fact that he'd received a telling phone call, like he had when I'd skipped school, only he'd be backed up by superheroes.



The last big conversation in that vein had done irreparable damage.  Enough that I found myself checking my house and making sure there wasn't an ambush waiting for me on the other side.  On my dad's side of things, well, we'd just discussed that in some depth.  Our relationship wasn't any better for it.



Taking time away from everything else I had to do, to eat lunch, to fill in the details and arrange things so my dad didn't discover I was bending the truth yet again?  To have another awkward conversation?



I was willing.  ``I'd really like that.''



He smiled.



I grabbed the notepad by the phone that we usually used for writing down numbers and put down my cell number.  ``Call me when you're coming around, so we can find each other.''



``Your cell phone?''



``Yeah.''



He looked sad for a brief moment, then perked up a little, ``I suppose you need it if you're going to stay in touch with the others.''



``Yeah,'' I said.  ``I should go.  I want to get a light run in and maybe catch up with some people before I start working.''



``Take care of yourself.  I'll be in touch around eleven or eleven thirty.''



I nodded.  I gathered a billfold with some ID and cash, a fresh tube of pepper spray, and then a sheathed knife from the backpack that hung by the back door.  It wasn't my good knife: I wouldn't be able to explain how I had a knife of that kind of quality.  This one was serviceable for self-defense, the kind that was currently being worn by countless people around the city.



I glanced at my dad, but he seemed to be going out of his way to avoid looking as I did everything necessary to prepare myself for venturing out into the city.



Was it him suppressing his worry for my well-being, or were my doubts on target?  Did he suspect, and simply not want to know for sure?



I couldn't ask, couldn't hint or try to get clarification, not without potentially seeding the idea in his mind, or prompting him to give me an answer I didn't want to hear.



I stepped outside, and the hot air was like a physical barrier.  I'd known it, had anticipated it with the knowledge my bugs provided me, but there wasn't anything quite like that first faceful of eighty-five degree weather, so humid it went straight through both skin and clothing.



The second I was out of sight of the house, I had my phone out.  I re-checked the messages that had come in last night and this morning.  Twenty in total.



Charlotte:
I know its already pretty late, not a big deal, but was wondering if u wanted to go out and grab ice cream?  terrys craving some.  we can grab jelly beans and a chocolate for my brother on our way back.



Charlotte:
eric stopped by.  no drama.  you should say hi while he's around.



Forrest:
saw Eric 2nite.  shuld say hi.



Forrest:
n/m Char already sent you msg.



Charlotte:
taking my little brother to school today.  if I dont see u, have a good day, will see u tonite.



All code.  Mostly code, anyways.  The names dropped were a shorthand for specific kinds of situations and people.  `Eric' was trouble.  `Little brother' meant the kids Charlotte was looking after.  `Terry' was the catch-all term for people in my territory.



There were two for me, as well.  `u' and `you', as odd as it sounded.



People were probably craving some luxuries in the food department and some treats for the kids wouldn't hurt.  There was some kind of trouble while I'd been out, but it was handled and I should pay a visit in costume to make sure it was resolved.  Charlotte would be going to school, taking all the little ones with her.



There were other messages.  Among them, there was a mess of some sort one of the side streets hadn't been cleaned up and `Terry' had been complaining, there were some vague concerns about the food supplies for lunch later today, and Lisa had called about a nebulous `party'.



I ran the rest of the way to the Boardwalk.



There weren't many people up and about yet.  Some cars on the road, the sounds of construction starting to get underway, and some parents with kids to see off to school and no cars getting an early start.



I passed by my headquarters and found someone unfamiliar inside, in the main room with Charlotte.  She was helping a little boy put a shirt on.  Forrest was in the kitchen, mass-producing kids' lunches with the supplies I'd had brought in yesterday.



I made my way to the beach, entering the storm drain that led, in a roundabout way, into my base.



The original plan, as far as I was aware, had been for this entrance to be temporary.  Work would continue on the Boardwalk, and it was inevitable that someone would run into the storm drain, either where it was deliberately blocked off or entering from the beach as I was.  It would have changed, with Coil leveraging his resources to set up something else that would serve as a covert entrance.



I'd have to contact Tattletale, though she was probably busy enough that \emph{my} to-do list looked trivial.



Bugs flowed down the stairs, surrounding me as a thick cloud that would hide me from sight. I could sense the kids reacting as I made my appearance.  Fearful starts and backing away, taking shelter behind Charlotte.



I singled out a handful of butterflies and sent them towards the kid nearest me.  They flew in formation, forming a circle around her hand.  She stretched it out, and one butterfly landed on her thumb.



As other children reached out, I settled butterflies on their hands as well.  The distraction was good enough that I could walk past them and head upstairs without causing anyone to burst into tears.



I locked the door behind me and quickly changed.  I draped the shawl-cape over my armored shoulders, and then covered it in bugs.  Wearing black in the summer would be uncomfortable, especially with the added heat and weight of the bugs, but maybe I could provide myself with some shade using a swarm overhead.



It would make me a target to any heroes paying a visit, though.  The PRT had recognized the potential for trouble that surrounded the door, Tattletale's improvised portal to another universe, and out-of-town capes were being given permanent positions on the local Wards and Protectorate teams. It said something, given the state of the PRT these days, that they were willing to devote the manpower.



A pair of villains from the Fallen were lurking somewhere in Imp's territory, and their presence meant that Haven felt obliged to send two or three capes our way as well.  Until the Fallen were dead or gone, Haven would have something of a local presence.



I'd done my part to try to help find the two Fallen, just a few days ago, but even with Tattletale's help in identifying the general area, I hadn't been able to root them out.  Her gut told her that one of the two was Valefor.  Despite the intimidating names and the fact that they called themselves an Endbringer cult, the Fallen didn't pose a grave threat.  They were thieves and vandals, allegedly committing incest in the belief that it would guarantee that their entangled family produced more kids with powers, but only a few people in the controlling body of the family were demonstrably capable of murder.  They were far from being the Slaughterhouse Nine.



Still, both Imp and Valefor were what the PRT termed `strangers'.  Capes with abilities that tended towards subtlety and subterfuge.  That wasn't a fight I wanted to get caught up in.  I would if it came down to it, if people were in danger or Aisha needed my help, but I was perfectly content to \emph{not} be in a position where I was looking over my shoulder every few seconds.  I'd dealt with that enough.



All of that wasn't even touching on the other villains seeking a foothold in the city.  The Ambassadors were looking for a slice of the Brockton Bay pie, and both Grue and I were tentatively willing.  The group of villains was willing to play by our rules and participate in our alliance, they would add their own strength to ours, and they were more interested in shady but legitimate dealings and preying on other villains than they were on causing trouble or bucking with the local authorities.  I couldn't be entirely sure whether that was because of their general ethos or because they were recuperating from being nearly wiped out, but their simple existence and their membership in our alliance would help scare off troublemakers.



It all added up to making the Ambassadors as ideal a partner-group as we could hope for.  The only sticking point was that their leader was a Thinker, and Tattletale almost automatically disliked him.  It would take a great deal more convincing to get her to play along.



The Teeth had tried to take a bite out of Parian's territory.  They had a history in the bay, and like the Ambassadors they had been nearly wiped out, only it was nearly a decade ago.  They'd settled elsewhere while they bounced back, with a turnover rate high enough that none of the original members persisted.  There was only the name, and an ethos of violence, anarchy, and profit at any cost, not unlike the ABB.  Parian seemed to be making a point of not asking for our help, and I wasn't intending to offer it until she did.



I had others to take care of, and I could only trust that she knew what she was doing.



``Skitter,'' Charlotte said, as I returned downstairs.  I could see the other girl, plump, with a shorter haircut that only seemed to accentuate the roundness of her face.  She seemed more scared of me than the kids were.



Forrest, by contrast, was almost bemused.  He leaned over the kitchen counter.  He had a barrel chest, a burly build, a natural glower, a thick black beard and coarse, unkempt hair.  He might have looked savage if it weren't for the tight-fitting striped polo shirt and the nerdish thick-framed glasses.  It hadn't been that long ago that he'd helped sway the outcome of my fight against Mannequin, putting his life on the line to help take down a monster that even some top-tier \emph{cape}\emph{s} had been scared of.



I'd asked Charlotte to find someone who could serve as my second in command.  I considered it serendipitous that she'd nominated \emph{him.}



``Any urgent issues?'' I asked.  She shook her head.  I let myself relax a touch and gestured toward the new girl, ``Who's this?''



Charlotte looked guilty.  ``She's an extra set of hands.  Don't worry.  Forrest and I blindfolded her while bringing her here.  I didn't think I'd be able to manage looking after the kids all by myself, and I was ok with paying her.''



``I can cover that cost,'' I said.  ``No trouble on that front?  Taking care of the kids?''



``We're just about ready to go,'' she said.  ``Kids are washed, fed and clothed, lunches nearly finished.  They have their bags\ldots''



``Good,'' I said, ``The school bus is arriving soon.  Can you spare a minute to fill me in?''



``I can't even remember all of the stuff that's been going on.  I'm kind of frazzled.''



I felt a pang of sympathy.  This was the cost of me staying with my dad.  ``The pertinent points only, then.  Who or what is the `Eric'?''



``Forrest can explain.  Some thugs were causing trouble for some people living further north.  Your guys caught them.''



``The mess in the alley?''



``The garbage trucks couldn't get down the road.  Shale avenue is still in rough shape, and nobody told the residents they shouldn't put their trash on the sidewalk there.  It's piled up and it's hot, so it's smelling.''



``I'll resolve it.''  \emph{Wasn't so long ago this whole city stank, and people weren't complaining this much then}.  ``The lunch supplies?''



``One of the pallets of vegetables you ordered was in bad shape.  Past ripe.  I'd planned to have something done last night that Forrest could warm up for people's lunches today, but I couldn't work with what I had, and I thought you'd want something better than a thin soup.  Then I was occupied looking after the kids and forgot.  I'm sorry.''



``It's fine,'' I said.  ``You've done an excellent job.  Better than I could have hoped.  I'll figure something out for lunch.  Maybe reach out to a local business.  What's a food most people would enjoy, which we haven't had available for a good while?''



``Pizza!'' one boy in Charlotte's herd of children piped up.



``Pizza it is,'' I said.  ``With luck, there's someone trying to get set up somewhere in the north end.  We can order a batch for everyone that's working here, then another batch for tonight, for the kids?  \emph{If} they're good in school and they do their homework.''



The children almost \emph{crowed}, and one literally jumped with glee.



``Forrest,'' I said.  ``Can you see them off to the bus stop?  I need to have a word with Charlotte.''



Wordless, Forrest stood straight, gathered up the paper bag lunches in two hands and then approached the kids.  Like magnets, two kids gravitated to his legs and clung to him, and he walked stiff-legged to the front door with them hanging on him and the rest trailing after him like my bugs trailed after me.



My bugs kicked into motion, blocking the line of sight to the door.  No use giving Charlotte's friend a view of the street outside and a clue about our location.  She made a small frightened sound and backed away.



\emph{Did Charlotte honestly bring in someone who's afraid of bugs?}



I glanced at the two girls.  Charlotte's eyebrows were knitted in concern.  Her friend, by contrast, looked terrified: her fingers were knotted together, her eyes wide.



``Jessie's still wetting the bed, I see,'' I noted.  My bugs could feel the damp on one of the bunk beds in one of the other rooms.  \emph{Something mundane, so we don't frighten the new girl further}.



Charlotte's eyes widened.  ``Shit!  I was so busy trying to get things organized--''



``It's fine,'' I said.  ``I'll handle it.''



``You shouldn't have to,'' she said, ``Fern--''



``That's the other thing I wanted to mention.  Your friend--'' I glanced at the girl.  She didn't look any less spooked.  \emph{Why did Charlotte bring her here if she's going to be so afraid}?  ``Did Tattletale vet her?''



``It was a spur of the moment thing.  I know it was sorta dumb, but--''



``I don't want to be hard on you,'' I said, ``But this is something I'm going to be strict about.  Someone comes here, they have to be vetted first.''



``I'll be more careful.''



``Please.  And are you \emph{sure} there isn't anything I can do to thank you for your help?''



``You're paying me more than enough.''



``Let me know if anything comes to mind.  In the meantime, pizza and some candy for the kids tonight?''



``It's tough, going back to school, trying to get back to something even \emph{resembling} a normal routine.  They'd appreciate it, I think.''



``Okay,'' I said.  ``Don't mention the candy.  Let it be a surprise.  I think the bus is coming, so you should head to the stop.''



``Blindfold on, Fern,'' Charlotte said.



A minute later, they were gone.



I sighed and set to tidying up.  Bugs carted away the unused paper bags and scraps of lettuce.



\emph{And everyone's off to school}, I thought.



I felt a pang of regret.  A part of me wanted to go, to prove to myself that I'd grown past it, to have another \emph{normal} thing in my life, like breakfast with my dad.



At the same time, there were so many reasons not to.  My face having been exposed in a roundabout fashion, the presence of the Wards somewhere in that school, the time it took away from other things that needed doing\ldots



Better to keep out of it.



Forrest returned.  ``Want to see 'em?''



I nodded, and we ventured out into my territory.



All around us, the Boardwalk and what had been the shadier parts of the Docks were coming together.  New streets, new sidewalks, new buildings.  There were more people out and about than there had been just ten or fifteen minutes ago, and everyone present was getting ready to work or even starting early.  Building something as a community.



Conversations died as I approached, power tools were turned off, and heads turned.



My bugs followed behind me like the trail of a fancy gown, rising from my shoulders and hair like pitch black sparks from a fire.  Image.  I'd done what I could to earn the loyalty of my people.  I'd tried to be even-handed, tried to be generous, but image and attitude was a big part in \emph{keeping} that loyalty.



I was put in mind of my dad's thoughts on a parent's authority.  Was this so different?



``The attackers were leftovers from the Chosen,'' Forrest explained.  ``I'm not even sure they were full members.''



``Is the family okay?''



``They're okay.  Scared, they lost a few possessions, but nothing really valuable.''



``The little things matter most when you have the least,'' I said.



``Profound.''



I couldn't tell if he was being sarcastic or not, and I couldn't see his face without glancing over my shoulder, so I didn't say anything..



The cells were hidden in one building, much like my base was.  A few of the O'Dalys were lingering at the front.  They stood at attention as I approached.  The closest thing I had to foot soldiers.



A Japanese couple stood nearby as well.  The man had a bandage across his nose, blood crusted around his nostrils.  Bruises stood out on both of them.



I walked past them to step inside, and looked at my prisoners.  Three thugs, no younger than fifteen, nor older than twenty-five.  They wore so much face paint I couldn't make a good guess beyond that.



My soldiers and the couple had followed me inside.



``You came for revenge?'' I asked.



``N-no,'' the man said.  ``I came to ask for leniency.''



``Fuck you, faggy ass fagass!'' one of the people in the cell shouted.



``For \emph{them}?'' I asked.



``Yes.''



``They hurt you.''



``Out of ignorance,'' he said.



``\emph{You're} ignorant, assfaggot!''



``My wife and I consider ourselves good Christians,'' the man said.  ``He would want us to show mercy, to turn the other cheek.''



``Why don't you spread those cheeks and get \emph{fucked}, faggot!?''



``Quiet,'' I said.  A handful of bugs flowed into the cell, the boy opened his mouth to retort and choked on a fly.  To the man, I said, ``You're tying my hands here.  I can't let them leave unscathed.  It would send the wrong message, and that would do everyone in this territory a disservice.  You, me, \emph{them}, everyone else.  People need to know they're safe, especially after everything that's happened.''



``The police can take care of them.  Call it a citizen's arrest.  We won't mention your name.''



``And if they go free?  If the police decide there's not enough evidence, or the officers are too busy to give your case their full attention, and these three get to go on and hurt others?''



``If that's the cost of having a system that otherwise works.''



I glanced at the three thugs, and my bugs flowed over them.  Silk was threaded in strategic locations, and bugs deposited where they wouldn't be able to reach.



``Open the cells,'' I said.



I could see the fear on the faces of the couple as they backed away.  Forrest pulled the switch, bidding the three iron-barred doors along the hallway to slide open.



One of the thugs glared sullenly at me, but he was smart enough to not mouth off.



``There's a small police office nearby,'' I said.  ``You three can head down Shale avenue, stop one block short of Lord street, and turn left.  It's a tent, and there's two officers and a police car there.  They'll take you into custody.''



``Right.  We'll \emph{totally} turn ourselves in,'' a second guy said.



``Do I need to repeat the directions?''



``Nah,'' the first one smiled.



``Go,'' I said.  My bugs cut the silk threads binding them to the bars.  If they'd lunged or tried to attack us, they would have fallen short, possibly choking or tripping.



``Seriously?'' Forrest asked.



``Cool shit,'' the lead thug commented.  He gave Forrest the finger as he headed to the door.  Forrest moved as if he was going to hit the punk, and the thug flinched, but there was no follow through.



They bolted the second they were out of sight of the O'Dalys who were stationed at the front of my miniature jail.



I commanded the bugs I'd planted on the three thugs to bite, then gestured for the contingent of people around me to follow me.



All three boys were still lying on the ground, writhing, when we arrived.  One was screaming as though he'd been jabbed with a hot poker.  Another was arching his back, as though his ribcage was trying to force its way free.



``What did you do?''  Forrest asked, in mixed horror and awe.



The third thug's screaming joined his friend's.



``Bullet ants,'' I said.  ``Their bites top the scale in terms of sheer pain caused.  People have compared their bites to being shot.  Thus the name.''



The thug was still screaming, albeit with less volume and more intermittent whimpers.



``It's also known as the twenty-four hour ant,'' I added.



``Why?''



``That's how long the pain lasts.  Get up,'' I ordered them.  ``\emph{Now}, or you get bitten again.''



It took them a second, but they were making a halfhearted effort, and I didn't follow through on my threat.  They stood, one of them hunched over, two moaning audibly.  They glared at me.



``You brought that on yourselves,'' I said.  ``This is your second chance.  Get yourselves to the police station and turn yourselves in.  This time, I'll have them bite each of you periodically to hurry you along.''



``What the fucking--''



He broke off mid-sentence as he screamed and fell to the ground, thrashing.



``If you think of doing anything but admitting your full crime to the police officer right then and there, I'll try figuring out how many times those ants can bite you before they run out of venom.  Now go.  \emph{Run}.''



Two of them ran, stumbling as they twitched and flinched at the continuing pain, while the third crawled.  I had an ant bite the mouthiest one when he was only a few paces away, to hurry them along.



I turned to the others.  The Japanese-American man was staring at me.



``You should go to the police too,'' I said.  ``Give your side of the story, let them take photos.''



``I will,'' he said, his tone curt.  He turned to leave, then paused.  ``I asked you to be lenient.''



\emph{How can I even explain?  I've seen the worst of the worst.  I want to protect each and every one of you from it.  The system won't stop them, not all on its own}.



But if I explained, they would argue, and every counter-argument would make me look weaker, damage my image and hurt people's confidence in me.  There were people who would be \emph{happy} with a firm hand being used to deter criminals, there were others who wouldn't be happy, but they'd accept it as the price that came with everything else I had to offer.



I didn't like it, but I'd do it.



He was still staring at me, his question lingering.  \emph{I asked you to be lenient}.



``I was,'' was all I said.



\sectionbreak



I returned to my lair, and took the time to strip out of my costume.  It stuck to my skin as I pulled it off.



I'd need to design something lighter for the warmer months.  More porous, while still offering protection, maybe a paler color, if I could manage it and still have it blend into the swarm\ldots



The major tasks were done.  I'd called Lisa, and through her I'd gotten caught up on all the other essential details about what was happening around the city.  She and Grue had a meeting with an Ambassador – not the \emph{leader} of the Ambassadors, which I was thankful for.  I would have wanted to be present for a meeting that volatile.  As it was, I could hope that Grue was in a good enough headspace to keep Tattletale on course.



I'd contacted everyone necessary to clear garbage out of the alley, to order pizzas for lunch and to order more food in to make up for the bad batch of vegetables.  I'd shown my face as Skitter and now a swarm-clone lingered on a rooftop, standing in plain view of the people on the street, overlooking a construction in progress.  `Skitter' would appear here and there over the course of the day, just to reassure others she was here.



Which she was.  \emph{I }was.



I stripped out of the rest of the costume.  I laid out a grungier change of clothes.



I hadn't been lying to my dad when I said I'd work.  I'd put in the hours, work alongside the other members of my territory.  It was easier to do my share and be working here on a legitimate basis, even part-time, than to try to sustain the lie.



Before I started, I had only one minor chore.  I headed downstairs and I pulled Jessie's mattress off the bunk bed, dragging it into an open space so I could clean it.  The mattresses were thin, and would dry after a day in this heat.  The humidity was a problem, but I could put it in direct sunlight.



My phone buzzed, still in the utility compartment upstairs.  My bugs brought it to me.



Charlotte:
I met someone in class.  I think it could be big Eric?



Big trouble?  I contemplated sending a reply, but the next text wasn't far behind.



Charlotte:
says hes an old classmate of urs.  asking where u are.  loud insistent intense.  wouldnt believe that u werent at school.  sounds like he might want to talk to you.



I didn't miss the distinction.  `u' meant Taylor.  `you' was Skitter.  If this person was careless enough that Charlotte had caught on\ldots \emph{Fuck}.





