





It couldn't be easy.  No.  Everything was finally starting to settle down, and then this.  Inconvenient timing, inconvenient in every way.  It had to be at the high school, of all places.



Tattletale and Grue would be meeting with the Ambassadors soon.  That took them out of the running, as far as people I could call.  Forrest was just a little too old and a little too attention-grabbing to be seen lurking around the local high school.  Regent, Imp or Bitch?  I was trying to \emph{fix} the situation, not make it worse.



I pressed Charlotte for more information:



RT:
You see him?



Charlotte:
no.  no bars here. had to leave to make call.



Right.  Arcadia was one of the schools that had a Faraday cage, if I was remembering right.  Something to stop kids from texting and making calls in class.



RT:
What was he doing?



Charlotte:
asking about u in hallways, checking with ppl to see if u were around.



Charlotte:
i approached him and asked how he knew u.  he said he didnt.  seemed too intense for that so i called u.



RT:
GJ.



All in all, almost exactly what I might have told her to do if I'd been in direct contact with her at the time.



RT:
This is Eric with blond hair?  Blue eyes?  Talks like he's going to run out of breath and pass out?



Charlotte:
Yes.



My suspicions were confirmed.  Greg.



Charlotte:
is break btween class atm.  have 2 go soon.  what shld I do?



No time to think or plan.  It was annoying how these codes and protocols that Tattletale and I had come up with were costing us precious seconds.



RT:
Go back inside to see if there's drama.  Tell him I'm not at school, if you can, but that I can meet him later.



Charlotte:
k



While I waited, I patted the mattress dry where the cleaner had soaked into it, then dragged it upstairs.  My phone buzzed before I'd dressed to take it out to the balcony.



Charlotte:
he gone.  class starting.  no drama I can see.



Damn.  Not as bad as it could be, but the situation wasn't resolved.



RT:
What's your next class?



Charlotte:
Eng.



RT:
Go.  I'll see if I can track him down.  Will find you if I need you but don't worry.  Good job.



I'd let her return to business as normal: I didn't want her too caught up in this.



There was something to be said for having good help.  I felt more than a little guilty.  Much like Sierra had during the worst periods, Charlotte was picking up my slack.  In managing my territory while I was going home to sleep at my dad's house, she was earning her wage twice over.  I would have increased her pay but she didn't want me to, claiming it would arouse suspicion.



Maybe I could get Tattletale to arrange some kind of scholarship for her.  We had funds.  Tattletale had acquired everything Coil had owned, and it had been easy enough to assume his false identities and take over the dummy corporations.  Now that the city was starting to pick up and people were talking about the potential the portal in the downtown area had, the land was skyrocketing in value.



Not to mention that the Ambassadors had given us a healthy lump of cash when they'd arrived in Brockton Bay, and were paying rent in the thousands of dollars so we'd be copacetic with them just being around.



Apparently that was villain protocol, in a way, doing jobs or giving gifts when intruding on another's territory.  I could see why: it let one ask for permission and show respect while still giving evidence to a measure of power.  If these guys were willing to hand over tens of thousands in the same way other people gave gift baskets, it showed they had that kind of money to spare, and they were \emph{confident}.  The side benefit for us specifically was that it kept Tattletale from complaining too loudly.



With luck, there would be others like them.  Which wasn't to say I \emph{trusted }them.



I dressed, pulling on my running shoes, a tank top and the lightweight cargo pants I'd worn to run.  I left the grungier clothes laid out on the bed, and made doubly sure I had my cell phone, identification and my knife.  I doubted I could have it in plain sight, so I stuck it in my sock and pulled my pants leg down around it.



It was nine fifty in the morning, and I figured I had an hour and forty-five minutes before the second class of the day ended and the lunch hour began.



I had to find a way to drag Greg out of class and talk to him without alerting others.  That, or I'd have to wait until lunch started and postpone plans with my dad.  Inconvenient.



The bus was running on a reduced schedule.  There were fewer intact vehicles, fewer drivers in the area, and routes were longer with the detours that they had to take.  It wasn't as bad as it might otherwise be: a twenty-minute wait.



I stewed in my own frustration.  There had been occasions in the past where I'd had to leave my territory to handle greater threats.  It irritated me more than it should have, to be forced to leave for \emph{this}.  Such a minor thing, but prickly enough that it had the potential to become something major if ignored, and awkward overall to handle.  How did I even approach the conversation?



\emph{I've faced down a handful of the scariest sons of bitches in the world, I've been intentionally trapped in a burning house, blinded, had my back broken, I've been paralyzed and at the mercy of no less than two lunatic} tinkers,\emph{ and I've killed a man}, I thought.  \emph{And going back to school stirs up old feelings of anxiety}.



I could feel the building tension and a shift back to old ways of thinking, and the \emph{ridiculousness} of it made me smile.  It was the middle of the morning, the bus was almost empty, and I stretched as though I were just waking up.  One or two people glanced my way, and I allowed myself to not give a fuck.



It helped, as though I were physically shrugging off the old burdens that were settling on me.



The wind from the open windows of the bus stirred my hair, and I exhaled slowly, turning my face into the sun, letting it warm me even as the breeze cooled me off.  I couldn't do anything about the time it took to get there, so I might as well take the opportunity to get a breather.



Arcadia High.  I'd seen it in the midst of some of Brockton Bay's worst days, but effort had been expended to fix it up and get everything sorted out.  New windows, that caught the light in a way that made them look almost like compound eyes.  Some kind of sub-layer or something worked into them that made for a number of quarter-sized hexagons.  The front gate had been rebuilt, cracks paved over, and vandalism cleaned up.  It was pristine, with panels of white tile and glass that almost glowed in the morning light.



The thing that caught me off guard was the \emph{people.  }Classes had started, but there were forty or so students gathered around outside, sitting and talking, texting or simply enjoying the sun.  A half-dozen adults in outfits that were uncomfortably similar to the enforcers of the old Boardwalk were stationed at the gates and at points around the school grounds that let them keep an eye on things.  Security?  Volunteers?



That wasn't the entirety of it.  The students fell into two groups.  One was very much what I might have expected, kids in new clothes or casual summer wear, smiling and talking.  Months ago, I might have felt like the smiles and periodic laughs were directed at me, and not in a flattering way.  I'd always\emph{ rationally} understood that they weren't, but not to the point that I could convince myself.  Now I reveled in my anonymity.  I knew what it was to have every set of eyes on me, people covertly trying to gauge who I was and what I was doing every time I moved a finger.  This wasn't it.



The other, larger group of students, adding up to maybe thirty-five of the forty kids present, was something else.  They were the Sierras, the Charlottes, the Ferns and the Forrests.  They were the Jessies and Bryces, the Taylor and Danny Heberts.  The people who had \emph{stayed}.



I just had to look at them, and I knew it.  Some had dressed in new clothes, but others wore the clothes that had weathered the last few weeks and months, worn and frayed at the edges.  Physically, some were frayed.  They had lines in their face that spoke to weeks with a bare minimum of sleep, and both skin and hair bore the coloration that resulted from days spent outdoors.



One or two, I noted, carried weapons.  One had a knife displayed visibly at his hip.  A girl with a burly frame very similar to Rachel's was sitting beneath a tree, eyes closed, her hands on a stick with an electrical tape grip.  There wasn't anything definable, only little clues that added up, and a general \emph{atmosphere }about them.



I didn't miss the division between the two groups.  The five or so fresh-faced teenagers weren't hanging out with the ones who had stayed.



``You just arriving?'' one of the enforcers at the gate asked me.



``Yeah,'' I said.



He studied me just long enough that I felt acutely aware of my bare shoulders and arms, and how my top clung to my stomach.  I glared at him, and he met my eyes with an ease that suggested he didn't care I'd caught him looking.  Creepy.



``Got a weapon?''  he asked.



``Yeah,'' I replied.



``Can't keep it if you want to go inside.''



I was only keeping myself armed as a matter of practice, and I was aware I wasn't alone on that front, or I wouldn't be doing it so casually.  I reached into my sock and withdrew the sheathed knife.  \emph{It says something that we can even take this conversation in stride}.



I handed it to him.  It wasn't worth the time it would take to argue.  ``What's with these people outside, here?''



He shrugged.  ``Easing into it.  We asked if we should round 'em up and take them inside, but the principal said we should give them a few days to depressurize if they wanted it.''



``Depressurize,'' I said.



He glanced at the knife, ``All I know is we're not enforcing a lot of rules yet.  Sometimes a few take a break and come outside, smoke, talk, get some fresh air and sun.  \emph{Those }ones don't tend to stay long.''



He was looking at one group by the front door, three of the ones who didn't have that weary, worn, and wary sense about them.  The ones who'd no doubt fled the city when things turned ugly.



\emph{I'm not the only one who sees the distinction, }I mused.



``I think they're intimidated.  Or you and I see it as a nice sunny day and they see it as being outside in a shithole of a city.''  When I didn't keep the conversation going, he shrugged, ``If you're going in, you'll want to go to the office.  They'll sort out where your classes are.''



``Okay,'' I said.  There was no need to explain that I wasn't here for classes.



By the time I'd reached the front door, a trio of teenagers younger than me had already approached the same guard.  It would be another litany of questions.



It did something to explain why the guards were there.  The two kids who hadn't been willing to part with their weapons were no doubt another part of that.  The whole dynamic was skewed, now, and they were mediating the worst of it.



I'd been in Arcadia High once, and it had been more of a life or death situation, one where I had been able to tentatively use my bugs.  In this unfamiliar territory, with a thousand or more students throughout the building, I had to actively work to suppress the powers I'd been using on an almost automatic level.  I couldn't be sure that a small cloud of flies would go unnoticed as they traced the contours of a hallway.



Much like I'd seen outside, there were a handful of students who hadn't yet made their way to class, or had stepped out for a breather, congregating in pairs and trios, or standing alone.



I knew I could have asked them for directions, but I wasn't keen on approaching people who were in the process of \emph{avoiding }socializing.  The men and women in uniforms that were stationed at the intersections where the halls met?  More of a possibility, but there was no need.  Directions were posted on the wall.



I glanced at a note on the wall.  One sentence, with no punctuation, and a big black arrow pointing one way.



New sudents go to front office



If I'd had a little bit of hope that things were working out here, they faltered some when I saw the typo.



I noticed another set of papers that were arranged on the wall, not because of what it said or the title, but the cartoon etched on the wall in permanent marker.



The heading of each of the sheets read `Know where you are'.  The paper with the graffiti was Rachel's; a crude drawing of a dog was violating one corner, which had been torn slightly to accommodate the dog.  A speech balloon over the smiling dog's head read `you don't know shit'.



Fitting, if it was one of Rachel's followers.



I headed in the direction of the office, feeling strangely out of place.  This entire thing was surreal.  There were the hallways with gleaming floors smudged by the passage of hundreds of feet, the bright primary colors in trophy cabinets and on bulletin boards, all contrasted with the security guards that were set up and standing to attention as though they expected a fight to break out any moment, and the innumerable teenagers who were being allowed to roam the grounds, some hanging around with weapons at hand.



But more than anything else, it was the notion of where I fit in the grand scheme of things.  Growing up, attending school, there had always been this general sense of the local gangs and powers and their influence.  It was the little things.  The gang tags scrawled on walls, the posters informing Asian students of who they could contact if the ABB started pushing them to join or pay tribute.  There had always been the rougher kids who wore certain colors and symbols of their affiliation.  It had meant something when a teenager wore yellow, or when an adult had an eight-ball tattooed on them.



I \emph{was} aware that Arcadia High had been scrubbed clean, and that things wouldn't become fully apparent until people had gotten more settled and more comfortable.  Even with that, though, it was unsettling to notice that for the first time since I was eleven, I couldn't see anything relating to the hostile gangs in the area.



There were no real gangs except for ours.  Grue, Tattletale, Bitch, Regent, Imp, Parian and I were the vague, intimidating forces that people worried about crossing.  We weren't as bad as some of the ones that had come before us, sure, but people still saw us as something to warn others about.



I'd seen all the people working for me, sensed them with my bugs.  I'd read about myself on Parahumans Online, and in news articles.  At the same time, high school was sometimes described as a microcosm of the world at large.  There was something else about being in the midst of a three-dimensional model of it all, seeing it have a concrete impact on a place that was more familiar.



Four teenagers were sitting along the side of the hallway as I walked by.  They stared at me as I passed.



I had to work to reassure myself that there was no connection between what I was thinking and the fact that they were looking at me.



It \emph{did} remind me that the Wards were here, and whatever else had happened, they might have seen my face.  Not \emph{my} face, but they could easily have seen a deformed evil clone of me.



There was that surreal sensation, again.  Was it weird that I felt most like \emph{Taylor} at school?  That I was all the more cognizant of the weirdness of all the cape stuff?



They were still looking.  I gave one a curt nod, and she nodded back.



I quickened my pace as I headed to the office.  I wanted to be \emph{gone}.



There were a lot of students in the office, and I was soon aware of why.  There were capes present.  Ones I only barely recognized.  Adamant and Sere.



``Listen!''  a woman behind the counter raised her voice to be heard over the general babble.  She had more authority than I might have expected of a secretary.  ``Get in a line! If you're here to look at the superheroes, you can do it later!  They'll be here all week!''



Nobody listened, of course, and the secretaries weren't really helping, taking requests and giving out information to whoever was closest to the front.  It only encouraged the press of bodies.



I headed to the other end of the room, hoping I'd be able to work my way around the end of the crowd.



I glanced at the clock.  Ten-forty.  I had maybe twenty minutes before my dad called me, and getting back in time would be difficult, even if I was lucky enough to have the bus show up at a convenient time.  I could postpone, plan a late lunch, but I \emph{really} didn't want to.



``Please,'' Adamant spoke, and his voice was filled with confidence, ``Do as Principal Howell is asking and form lines.''



\emph{That} worked, but not all that well.  People elbowed and pushed against me as we arranged ourselves into loose columns.  I'd never liked the feeling of being in a press of bodies, and it made me think of other unpleasant situations: Bonesaw straddling me, being drawn into a massive, monstrous lump of flesh.  It made me exceedingly uncomfortable, and being uncomfortable made me instinctively reach for my bugs.



That was another reason to not be in classes.  How long would it be before my power did something while running on autopilot and drew attention?



I studied Adamant and Sere while I waited.  Adamant, naturally, wore a metallic costume, featuring metal bands and panels that were loosely linked together by chains, fit over a black bodysuit.  He'd been at the fight against Leviathan, if I remembered right.  He was a member of Legend's team in New York.  Or he had been.  Legend was gone now.



Sere wore cloth, in contrast to Adamant.  He wore a kind of nomadic, desert-tribe style of robe, all in pristine white with a fine pattern embroidered onto it.  His mask was more stylistic than representing anything, a solid white plate with light blue lenses for the eyes and no opening for his nose or mouth.  What made him stand out was the moisture that flowed from the gaps in his handwraps and from around his mask.  It swirled around him like a breath outdoors in winter, pale.  Almost an inverse of Grue.



Powerwise, I knew Adamant was a bruiser, though I didn't know the specifics.  Sere, I did know about, but only because I'd once come across a cell phone video of him brutally taking down a number of thugs, posted online somewhere, months ago.  Some capes shot fire from their hands.  Sere was the opposite – he could draw moisture to himself with surprising speed and violence.  It didn't matter if a foe was armored or behind a forcefield, he could dehydrate them in a flash.  It was the kind of power that might have earned him a villain label if he hadn't had all of the Protectorate's PR at his back.



I idly wondered what had made the pair stick with their employer, in the wake of the recent events that had so many leaving the Protectorate with little to no explanation, Legend among them.



More than that, I was wondering how I'd fight them if it came down to it.  With the way the armor and chains of his costume were arranged, Adamant was just \emph{begging} to be tied up. Sere would be trickier.



``You're next, black curls,'' the secretary closest to me spoke.



I focused my attention closest to her and approached the counter.



``What do you need?''



``I need to get in contact with someone.''



``We can't give out personal information.''



``Not even if it's an emergency?''



``If you need to inform a student of something critical, we can make an announcement.''



``No.  That'd be the opposite of what I need to do.''



``You could always look for them during the lunch break.''



I frowned.



``If there's nothing else, there are others in line.''



``What's the procedure for signing up for classes?''



``You tell us your old schedule.  We slot you in as well as we're able.  Core classes are in classrooms.  We've adopted another system for non-core classes.''



``Non-core?''



``Anything besides maths, science, phys ed, and all those.  Non-core classes are held in the computer labs.  You'll have a rushed curriculum, alternating reading assignments with quizzes and worksheets on the computers.  There are teachers at the front of the lab if you have any questions.''



``I don't suppose you could tell me all the classes that are second period?''



She gave me a stern look.



I was feeling the pressure.  This maybe wasn't the brightest move, but I wanted to find Greg, get this solved, then return to life as normal.  Lunch with my dad, in an ideal world.



\emph{What classes did Greg take?}



I could remember him talking in Spanish.  God, it felt like years had passed, not months.



``World issues--''



``Grade?''



``Ten.  World Issues, Spanish\ldots''



\emph{Not English.  Charlotte's in that class and she probably would have slipped out to send me a text}.



``\ldotsHistory and Music,'' I finished, picking two more that weren't likely to be on the computers.



``World issues is a non-core class.  That'll be your fourth period.  You have History now.''



She struck a key and the sheet began printing.



``You don't need my name or ID?''



``We have zero notice on who's going to be here or not.  For now, everyone is to go to classes.  Do your best to catch up for the tests in one week, where we evaluate where everyone is.  We're adding students to the system on a priority basis.''



I nodded.  Something of a relief, that this wasn't set in stone.  She handed me the paper and I took it, turning on my heel to head out of the office.



\emph{Computer labs first}, I thought.  I hated to do it, but I drew on my bugs to find the labs in question.  With my luck, Kid Win would have put something together something to track unusual bug movements, and I'd get found in a second.



The first lab was a bust.  Nobody got in my way or spoke up as I entered the room.  There was only an older teacher who pointed wordlessly at a space where computers were unattended.



I walked up between the rows and looked at the students.  No luck.  I left through the back door at the other end of the class.



Halfway through the second lab, I saw Emma, clustered with a group of others.  Her hair was dyed blond, done up in a french braid, and her clothes were brand new.  Their eyes were on a computer screen where they were watching a video on a streaming site.  I wasn't surprised that she'd drawn people to her so quickly.  She had that magnetism to her.



She looked up and noticed me, no doubt expecting to see a teacher, and I could see her eyes widen a fraction in recognition.



But I was already walking, moving on with my search.  She wasn't a priority.  I deposited a single fly in her bag so I could keep out of her way and headed out of the room.



Ten minutes passed as I moved from area to area.  I was aware of the moving timeline, and felt a knot of anxiety in my stomach that had nothing to do with school.



Fuck him.  Seriously.



By the time I found him in the smaller gymnasium, where long tables and computers had been arranged to form an impromptu computer lab, it was past eleven.  My dad would call any minute.



I walked up to him and tapped him on the shoulder.



The change in his expression when he saw me, with the spreading smile of a child that had torn open the wrapping paper to find the very present they'd wanted\ldots fuck me.  I could see where Charlotte had been concerned.  There was zero subtlety to him, and a bare minimum of restraint.  Or maybe it was the other way around.



He pointed at the door, and I nodded once by way of reply.  I headed in that direction without waiting for him.



\emph{At least he didn't blurt out `Skitter!' in front of everyone.}



``I can't believe you came, you--''



Seeing his awe, the unrestrained excitement, I decided on a strategy.



``Are you stalking me?'' I asked, cutting him off.



I could see his expression change, shifting from enthusiasm to confusion.  He looked decidedly deranged for the split second he was midway.



``No,'' he said.  ``The reason--''



\emph{Can't let him get going or it's all over}.  \emph{He'll keep talking until he says something we'll both regret.}  ``Then you have a grudge against me.  Some vendetta or something?''



``No!''



``Because you barely know me, and a friend said you were being seriously creepy with the way you were trying to get info on me.''



``I wasn't!  I was trying to help!''



\emph{Help?}



I fumbled for a question that wouldn't give him an excuse to say anything vital aloud.  I felt like I was channeling Rachel as I spoke, ``I don't need your help.''



``I--''



``In fact,'' I cut him off.  ``I'm offended you would say it.''



``\emph{I know}!'' he \emph{strained} the words at me, two words said in a way that was too excited to be a successful whisper.  He wasn't talking about me being offended.  He was talking about my secret identity.  Fuck me.



``Greg,'' I said, reaching out to put the flat of one hand against his shoulder, as if pushing him away, ``You don't know anything about me.''



``We're not that different,'' he said.  He'd shifted gears to bewilderment.



``In what way are we the same?'' I asked.  Safe question, unless his answer included a confession that he had powers.



``We're\ldots not social people.  We like reading,'' the answers were weak, and from the look on his face, he knew it.  There was a benefit to him being this transparent, and I was counting my blessings that he wasn't very good at articulating what he was thinking.  ``We like computers.''



And, fuck me, I couldn't help but admit that he was \emph{nice}.  Part of the reason he was struggling to provide an answer was that he was couching his statements to avoid hurting my feelings.  The answer was short: we'd both been the losers, but he wouldn't say it outright.



I let him flounder for a little bit longer.  I didn't want to tear him down, but every second that his confidence wavered was an advantage to me.



``You don't know anything about me,'' I repeated myself for effect, then quickly added, ``You kind of messed up my day doing this.''



With the reaction I got, someone might have thought I'd slapped him.



``I wanted to help,'' he said.



``I was \emph{spooked},'' I said, feeling like shit even as I continued to leverage his better qualities against him.  ``All I got was a friend texting me to say someone's looking for me like they have a vendetta.''



``That's not it\ldots'' he said, trailing off, but his enthusiasm was crushed.  He was visibly sagging, as though someone had let the air out of him.



``And I found out it was you, and all I could think was that you were angry and you wanted to hurt me, or maybe you had some crazed infatuation with me and you were stalking me.''



I could see the look on his face.  Horror mixed with panic.



``Fuck, Greg--''



``No.  That's not what it was--'' he said, breathless.  His face betrayed the lie.  It was at least part of it.  ``It wasn't like I was crazy over you, it was a little thing, a while back.  That's not--''



``I have a boyfriend,'' I blurted out the words in my haste to cut him off again.



It was like kicking a dog.



He went silent, and I took the opportunity to get my mental footing and plan out what to say next.



A boy stopped in his tracks on his walk way down the hall.  A little shorter than me, red haired.  Apparently our atmosphere was screwed up enough that he'd noticed.  ``Problem?''



``It's okay,'' I said.  ``We're in the middle of resolving it.  Personal stuff.''



``That's--'' Greg started, then he stopped, looking at the boy.  Even he wasn't so clueless as to say something in front of a stranger.



The boy looked between us, and then gave me a curious look.  He was one of the ones who'd stayed, I could tell at a glance.  Unlike some, though, unlike \emph{me}, he hadn't gotten much sun.  Odd.  Maybe he'd holed up in a house or a shelter for the last few months.  Staying indoors would have been safest.



From the way he was looking at me, I wondered if he saw something like that.  Difference was, I had a secret to keep.



``Thank you, though,'' I told him, before he could figure anything out.



He took it for what it was: me saying `\emph{go away' }in the politest way I could manage.  He left.



``Greg,'' I said, ``I don't want to hurt you and I don't want to be your enemy.  You have to understand, the last while has been \emph{scary}.  I'm guessing you didn't stay in town?''



``I did,'' he said, then he stopped, breaking eye contact.  ``I was on the outermost edge of the city.  Other side of Captain's Hill.''



\emph{There's a mountain on the far side of Captain's Hill}, I thought.  Which meant he wasn't close enough to matter.  I would have hesitated to call that area a part of Brockton Bay, but I could see where maybe Greg had convinced himself it was close enough to count.



``You didn't stay in town, then,'' I said.  ``That's fine.  Smart.  But maybe you don't get what it's been like here.  All I want is peace and quiet.  I want to spend time with my dad, who I very nearly lost.  I don't want trouble.  I don't want complications.''



``I was trying to help!'' he protested.



``Greg--''



He bowled over me this time, ``But I was thinking, you know, if I could figure this out, others could too.''



I glanced over my shoulder to ensure there was nobody in earshot.  A few fruit flies ventured out of a locker and checked around the corners.



``Greg, what is it you think you know?''



``\emph{You're Skitter,'' }he whispered.



``No, Greg,'' I said, calm, quiet.



``I was reading online, and it's like, there were people wondering if you were an adult, and it got me thinking what Skitter must be like in real life, and then it \emph{clicked}.''



That was just about the most horrifying thing he could have said, barring near-impossibilities like, `I got powers and I ate your hair to get pregnant with your child.'



``A \emph{feeling}, Greg?''



``It's more than that!  It all makes sense!''



``I was going to spend time with my dad,'' I said.  ``That was my whole goal for the day, it's my only goal.  I just want to unwind and relax after weeks and months of living in this hellhole of a city.  And you pull me away from all that because of a \emph{hunch}?''



``It makes sense.  Your age, your location, your attitude.  Even with the bullying, your trigger event--''



I cut him off, ``Trigger event?''



``Yeah, you--''



``What's that?'' I asked.



He stopped, trying to think of a way to parse the answer, and I could even see a flicker of enthusiasm, as he imagined explaining the concept.



The enthusiasm drained from his face.



``You're playing dumb,'' he said, but the confidence had taken a hit.



``You know that \emph{capes} hurt my dad?'' I asked.  ``Both times he got hospitalized.  Shatterbird the first time, the explosion at the town hall the second.   Superpowers are really the last thing I even want to \emph{think} about.  We can talk, but I really don't want to talk about the superhero stuff.''



Fuck me, I felt slimy, playing him like this, using my dad for leverage.



``I can't talk about \emph{this} without talking about capes.''



``About me being one of the villains?  Isn't it kind of insulting?  No, Greg.  I'm sorry, but you're wrong.''



``But the proportions, the appearance--''



``You're wrong,'' I repeated.  I was feeling enough sympathy for him at this point that it wasn't hard to inject some into my voice.



``Everything fit,'' he said, his voice small.



\emph{Fit, not fits}.  He'd already come to the conclusion I'd wanted.  I kept my mouth shut.  I wanted nothing more than to be gone, to arrange things so I could meet up with my dad with a minimum of questions, but I stood there and waited for Greg's response.



``I'm sorry,'' he said, in the end.



``You're not a bad guy, Greg,'' I said.  ``Sorry I'm not the person you wanted me to be.''



He nodded, mute.



``Take care of yourself.  Good luck with school.  Maybe I'll see you around.''



``I hope your dad's alright,'' he said.



``Thanks,'' I answered him.  Then I turned to leave.



God damned \emph{people}.  I felt like crap, both for manipulating him and the \emph{way} I'd manipulated him, but there'd been no other choice.  What the hell had he even expected?  That I'd admit it and be bursting with gratitude that he'd let me know I needed to take some extra measures with my secret identity?



Probably.



I headed for the front door of the school.  As crummy as I felt, I could relax a bit, now.  Crisis averted.  I'd send Charlotte a text, then see about meeting up with my dad.  I wanted to leave.  There was nothing for me here.  Only ugly feelings.



Except the difference from \emph{then} and \emph{now} was that I felt a hell of a lot more like an Emma than a Taylor.



Speak of the devil.  I could sense her by the front door, hanging out with a group of her new friends.  I changed routes and found a door in a stairwell, and stepped outside that way.



The problem was the gate.  A short wall surrounded the grounds, and I couldn't quite bring myself to climb it, not with the attention it would attract.  Going through the exit at the parking lot would take me in the opposite direction I'd wanted to go, and I was in something of a rush.



And maybe a part of me didn't want to \emph{run}.  Avoiding her was one thing, but going five or ten minutes out of my way to circle a whole city block just to keep out of her way was something else.



I walked briskly for the gate.



She saw me, walked to intercept.  \emph{Fuck her.  Of course she's starting something}.  \emph{It can't be easy.}



She placed herself between me and the gate.  She was almost playful as she stepped right, then left to cut me off as I changed direction.  I was forced to stop.



A sly smile was plastered on her face.  I was aware of the others looking.  The people who were sitting outside, the guards\ldots her friends were approaching to join her.



``Sneaky, sneaky,'' she said.  She looked like she was having a ball.  ``Trying to avoid me?''



I didn't reply.  I was a little spooked at how quickly my bugs were responding to my irritation.  Half of my psyche was saying `fight', the other half was saying `ignore her', and the bugs were only listening to the first half.  The second half was needing a bit of a push on my end.



There were few people in this world that had truly earned my \emph{hate.  }I'd put a bullet through the last one's brain.



Emma?  I couldn't care less about her.  \emph{That} was what unsettled me.





