





``\emph{Yes},'' I said.  ``I'm trying to avoid you because I have someplace to be.''



``I'm hurt, Taylor.  It's been a while since we had a chance to talk.  We used to be friends, don't you remember?''



``I remember,'' I replied.  Didn't want to get caught up in this.  At the same time, I wasn't sure I wanted to back down, either.



I glanced around at the others.  I needed a better term for the people who'd stayed, a name for that particular clique.  They'd approached us, interested, but were hanging back enough to indicate they weren't about to jump to my defense.  Couldn't blame them.  The last series of events in Brockton Bay weren't the sort that rewarded heroes.  These people had made it through by playing it safe and avoiding trouble.



Emma's friends weren't the same way.  They approached, offering Emma backup and support.  They didn't join in, though.  Emma was point-man here.  She was in a mood to start trouble, I could tell, and everyone present knew it.



The guards?  They hung back, even further away than the ones on the periphery.  Two or three of them.  As I saw it, they were backing \emph{Emma} up.  If I smashed her teeth in or tore her ear half-off like Sophia had once done to me, they'd stop me, and I'd get in trouble.  \emph{I'd} get delayed from getting to where I wanted to be.



``Changed your look?  I have to say, you manage to make any style look great.''



The sarcasm was subtle.  There was also a glimmer of a memory in there; she was referencing something.  I brushed it aside.  I doubted I wanted to think too hard on it.



``You're not impressing anyone,'' I said.



``So \emph{hostile},'' Emma said.  ``Is that part of your new image?  Being rude?  Keeping everyone at arm's length?  If anyone's trying too hard, it's you.''



Oh, I just had to take one look at her expression to see that she was \emph{reveling} in the irony.  She didn't give a damn that the accusations she was directing at me could be turned against her.  For her, it was all about the reaction she got out of me.  Victories, both big and little.



And all the while, she was oblivious to what I was holding back: tens of thousands of bugs, insects and arachnids, worms, centipedes, snails and slugs.  I restrained them in the same way I might keep my fist clenched, resisting the urge to swing it at her.



It wasn't just the idea of hurting her.  That was almost secondary.  It was the idea of catching her right \emph{now}, when she had less of a hold over me than she'd had in years.  To see the look on her face in the moment before the bugs forced themselves into her airways.  The dawning comprehension, the realization of what she'd brought on herself.



One action, and she might experience a share of the fear, the frustration and disgust I'd experienced over the years.  The hopelessness, the \emph{helplessness} in the face of someone with more power to throw around.



I could imagine the bugs flowing into her mouth before she thought to cover it, flowing into her nostrils until she covered \emph{that}.  I could imagine the moment she realized she'd have to swallow if she wanted to breathe.  I might even dismiss the bugs from flying around between us, just so I'd have a clear visual of it.  More likely that she'd throw up, but I'd have a minute or two before the heroes mobilized-



``Zoning out on me, Hebert?  Or did you spend too long outdoors and bake your brain?''



``I don't know what to say,'' I admitted.



``Big surprise.''



``\ldotsbecause I don't really think much of you anymore.  I've dealt with drug dealers, vandals, looters and thugs, and the gangs that were roving the city trying to get their hands on young girls.  Hell, I was there when Mannequin attacked the boardwalk.''



All true.  Except\ldots I `dealt' with them in a more direct fashion than I was implying.



``Big girl.  \emph{So} brave,'' Emma said.



I saw one or two people on the periphery of the crowd shift position, irritated.  They weren't my allies, not exactly, but Emma had just lost points, belittling what \emph{they} had been through.



``I have a bit more perspective,'' I told her.  ``I've seen how shitty people can be.  I've seen people who were desperate, fighting just to get by.  Others preyed on people, in the midst of it all.  I can't say I respect them for it, but maybe I understand it.''



``You're-'' she started.



I cut her off, talking over her, ``And the thing is, even after seeing all of the starving people, the ones who ate trash or stole to make it through the next twenty-four hours, I think less of \emph{you} than I think of them.''



I could see her eyes narrow at that.



``\emph{You're }insulting\emph{ me?}''



``I'm stating facts,'' I replied.  ``Talking to you even now, I'm realizing how small your world is.  You think of popularity and high school, of looking nice.  That's not even one tenth of a percent of what's going on in the world at large.  Yet you're trying \emph{so} hard to climb to the top of this tiny, sad little hill.''



``You're missing one key fact there,'' she said.  There was no smile on her face now.  ``You're beneath me on this little hill.  So what does that make you?''



``Emma, you're snarling at me and insulting me, trying to make jabs as if each little gesture will give you a higher spot on the totem pole, but there's \emph{no point}.  I'm not even a student here.''



``You're a dropout.  A failure.''



I sighed a little.  ``I really like this approach of yours.  You started off really subtle, and in the last minute alone, you've descended to flinging basic insults at me, trying to see what sticks.  Except I'm \emph{really} not bothered, and you're doing more to make \emph{yourself} look bad.''



Maybe I should have let her play it out a bit more and try a few more aimless jabs before I called her on it.  Didn't matter.



One member of her entourage piped up, ``Who do you think you are?  Talking to her like that?''



Another.  ``You think you sound so smart, telling her what she's-''



The girl stopped as Emma raised one hand.  Emma was glaring at me.  How long had it been since I'd seen anything besides glee and mean smirks?  Something \emph{substantial}, and not just a look of fear as she huddled with her family at some fundraiser, or being shocked when I'd slapped her in the shopping mall.



Was Emma actually \emph{angry}?



The Taylor of months ago would have appreciated at the realization, she might even have found it healing.  Not caring about what she said now came with an equal measure of not caring about her reaction.  I was almost disappointed.



``I've seen you break down in tears one too many times to buy that you don't care.  You're a wimp, Hebert, a coward.  You just want to look strong, pretend you're something other than what you are.''



``No,'' I replied.  ``I just want to go to lunch with my dad.  If you want to stroke your own ego, you can do it after I'm gone.''



I didn't feel \emph{better}, as this played along, somewhat in my favor.  I was still angry, I still wanted to hurt her, to see the look on her face.  But that feeling, in combination with what I'd mentioned to her earlier, when I'd said how small high school seemed in the grand scheme of things, it made my emotions seem out of proportion.  Monstrous.



And punctuating that monstrous line of thinking was the bugs.  Reflecting my feelings, it almost made for a throbbing sensation, insistent, the swarm working to move toward me, being pushed back with a semiconscious thought the next moment.



She \emph{was} getting to me.  It just wasn't the way she'd intended.



``You keep trying to run, Hebert, like a coward.  You should \emph{thank }me.''



``Thank you?  I'd love to hear this one.''



``God, if you just would have pretended to grow a spine a little sooner, everything would have been fine.''



``Somehow I doubt that.''



``People who stand up for themselves get respect.  If you would've tried this a little sooner, laughed more at the pranks and jokes, stood a little straighter instead of cringing like a whipped dog, it would have \emph{worked}.  We would've been friends again.  You'd have been part of the group, and things would have been peachy.  But you put it off too long, you made \emph{yourself }into a victim.  It wasn't \emph{us}.''



I could feel a few ideas fall into alignment.



``You're talking about Sophia.  You mean she would have let me into the group.''



``That's part of it.''



Now we were talking about Sophia.  About Shadow Stalker.  Emma knew that the two were one and the same, and \emph{I} knew as well, but I couldn't let on.



Still, it was leverage.



``That's a lot of it, I bet.  How demented are you, that you think I'd fucking want to be your friend, after all the shit you pulled?''



``Are you really better off where you are?''



``Now?  \emph{Yes}.  Then?  Fuck, even \emph{then}, yes!  I called you pathetic a minute ago, but Sophia's \emph{worse} than you.  She was a sad little basket case who lashed out at people with violence and barbed words because it was the only way she could deal.  The only real advantages she had were the fact that she was attractive and how you were misguided enough to look up to her, which is laughable unto itself.''



``Watch it,'' she said.



``I would've thought you were better than that, but \emph{no}.  She brought you down to her level, and you saved her from becoming a deranged thug, and made her a \emph{popular }deranged thug instead.''



One of her friends stepped forward, no doubt to bark a retort, but Emma pushed her away.



``Watch it!'' one of the guards called out.  ``Hands off!''



He was perfectly content to let this argument slide, but a push was too much?  Whatever.



Emma turned to her friend, ``Sorry.''



``Whatev,'' the girl muttered back.  She didn't look too happy.



Emma turned to me, and she had that mean, sly smile, like she had all the confidence in the world.  ``You want to play hardball, Taylor?''



``I \emph{want} to go meet my dad for lunch.  I've already said.  You've been playing hardball for years.  You can't really top using my mom's death to taunt me unless you're willing to pull a weapon.''



``Sure I can,'' the anger had faded, and she was cool, calm.  She seemed to relish her words as she said them.  ``You killed your mom.''



I didn't have a response to that.  My thoughts were momentarily a jumble, as I tried to process how that was even possible.



``Remember?  You were at my house when you got the call?  You were supposed to call your mom.  She was dialing for \emph{you} when she got in the accident.''



``Pretty weak, Emma.  I don't really buy it, and I don't think even you buy that I'm at fault.''



``Oh, but there's more.  See, your \emph{dad} thought so.  Your dad blamed you.  He \emph{blames} you. Remember?  He kind of disconnected?  Stopped caring about you?  You eventually went to my parents to ask if you could stay over some, until he found his feet?''



I could remember.  It had been the darkest period following one of the darkest moments of my life.



``My dad gave good old Danny a talking to, and your dad said he couldn't get over it.  He thought you were responsible, blamed you because you didn't make the call you were supposed to, and your mom had to drive over, worrying something was wrong.''



I could visualize it, fit this information into the blanks.



Emma continued speaking, and her words were in parallel with my own train of thought.  ``Ever think about how distant he got?  Maybe how distant he is, even now?  He loves you, maybe, but he hates you too.  He dished all the dirt to my dad, and told him how if you'd just called, if you'd picked up when your mom tried to call you from home, he'd still have his wife.  He'd still have a woman who was fantastic and smart and beautiful, someone \emph{way }too good for him.  Now all he's got is you.  You, who he took care of more because he \emph{had} to than because of anything else.  Does he even \emph{like} you, now?''



Did my dad love me?  Yes.  Did he like me?  That was up for debate.



A hollowness had settled in me.  I wasn't sure how much of it was what Emma was saying, how much was my thinking back to those days, and how much was an extension of the dissonance I'd been feeling since I stepped foot on school grounds.



I glanced at the others around us.  They were quiet, watching.  They weren't leaping to my defense or joining in on Emma's side.  Observers.



Emma, for her part, was smiling, mocking me with her smugness, waiting for the reaction.



I exhaled slowly.



With all the time I'd spent around Tattletale, it wasn't hard to see what Emma was doing.  Identifying the weak points, then making educated guesses, making claims that were difficult to verify, but devastating in their own right.  She didn't have powers, but she \emph{did} have the background knowledge of me, my dad and that period of my life.



If I'd ever been close to using my power on her, it was here, now.  The fact that she was using my parents against me?  Trying to fuck with me on this level?



I drew in a deep breath, then exhaled again.  \emph{Be}\emph{calm.}



Was it true?  Possibly.  But it would be next to impossible to verify, unless I was willing to discuss old, ugly memories with my dad.  Right here and right now, the information had only as much weight as I gave it.  I had to react to it like I might one of Tattletale's headgames.



``Okay,'' I said.  ``Are you done?  I'd like to go now.''



The anger was bleeding out of me.  If that was all she could do, on the spur of the moment, I didn't need to worry anymore.



The smile on her face remained, but it wasn't quite so smug, now.  ``I'm sorry.  I should have realized you're a heartless bitch.  You don't even care.''



``I don't think I really believe you,'' I replied.  ``But even if I did, whatever.  I've dealt with people who are smarter than you, I've had to handle people who are scarier and meaner than you.  I've even had to work with people who are better at manipulating others than you.  You don't have the slightest-''



I stopped.  My phone was vibrating.



There were too many possibilities for what it could be.  Issues with the Ambassadors, my dad, Charlotte\ldots



I turned away and answered the call, putting the phone to my ear.



``\emph{Taylor,}'' my dad spoke.



``Hi dad,'' I said.



``\emph{How's the work?}''



``It's not,'' I said.  ``I got a call from someone I've been working with on and off, and stopped by the school.  Where are you?''



``\emph{The boat graveyard.  We're trying to do some problem solving, and it's slowing us down.  Which school?}''



``Arcadia.  Want to meet me halfway?  The\ldots''



Through the single fly I'd planted on her, I could tell that Emma was striding towards me.  With only a split second to decide on a course of action, I decided to let her hit me.



She struck the phone out of my hand, and then shoved me into the wall that marked the perimeter of the school grounds.



Emma didn't say a word, but she was panting.  Was she trying to think of something to say?  She pulled me away from the wall, only so she could slam me against it again.



I could have laughed.  She wasn't strong, she wasn't intimidating.



I thought about saying something.  \emph{You're out of cards to play.  You've dropped past insults and you've descended to brute force, now}?



I didn't get a chance.  A guard advanced on us and pulled her off me.



The guard sounded almost casual as he kept a grip on the back of her shirt and one of her wrists, fighting to stop her from struggling.  ``Now we're off to see the principal.''



Figured.  I glared at him.  ``So you stand back until a fight erupts, and get both attacker and victim in trouble?''



``The job's to stop students from hurting others or getting themselves hurt.  Not about to step in the middle of an argument, or I'd be running around all day,'' he said.



``I'm not even a student here,'' I replied.



``Didn't figure you were, with how fast you were in and out.  That's why it's your call.  You can go, do that thing you were talking about with your family, or come back to the office with me and the girl.''



``What's the difference?'' I asked.



He shrugged, then grimaced as she continued to struggle.  ``We're supposed to take any troublemakers to the office along with students who might be willing to testify.  You're not a student, but maybe you plan to be, so it's up to you.''



I didn't respond right away.  For one thing, I was going to relish the sight of Emma \emph{finally} getting the short end of the stick.  For another, I couldn't shake the notion that this was some kind of trap.  For so long, it had been two steps forward, and one step back.  Why should things be any easier \emph{now}?



I picked up my phone and put it to my ear to see if the call was still connected.  ``Hello?''



``\emph{Taylor?}'' My dad was still on the other end of the phone.



``It's okay,'' I said.  I met Emma's eyes.  ``Emma tried to pick a fight.  They're taking her to the front office now.''



There was a pause on his end.  ``\ldots\emph{Do you need me to come?}''



``You said you were busy with something.  I doubt anything will come of this, so don't stress over it.  Want to meet tomorrow?''



``\emph{Okay}.  \emph{Good luck.}''



``Thanks.  Love you,'' I said.  The memories Emma had just stirred up flickered through my mind's eye.



``You too,'' he replied.



I hadn't taken my eyes off Emma.  She glared at me up until the moment the guard hauled her around, forcing her to march toward the school.



``You, in the sleeveless t-shirt, and you, girl with the haircut,'' the guard said, ``And you, the blonde in the purple shirt.  You're witnesses.  Inside.''  He'd named two of the people who'd been hanging outside, both with the telltale look of people who'd stayed in Brockton Bay, and one of Emma's friends.



There was some hesitation from a girl with the right half of her head shaved.  Her friends nudged her, and she joined the group.



Eyes were on us as we collectively headed in the direction of the office.  Emma pulled her hand free of the guard's grip, and sullenly marched at the head of the group.  Once or twice, she tried to change course, but the guard gave her a little push to keep her moving.  It meant that every set of eyes was on her from the moment where we entered the school to the point we reached the front office.



Principal Howell had given up on managing the late arrivals when we turned up, and was on the phone at the very back of the office.  Seeing us, she looked almost relieved to have a distraction.  One finger pointed the way to her office, and she quickly wrapped up her call, cupping one hand around the mouthpiece to drown out the babble of voices from the gathered students.



We had to take very different routes to get there, with the counter in the way.  By the time we arrived, she was seated behind her desk.  Emma and I took our seats in front of the desk, with the guard and the three witnesses lined up behind us.



The principal wasn't terribly attractive, and her roots gave away her bleached hair.  Just going by her appearance, and by the colorful blouse and scarf she wore, she didn't give me a sense of an authority figure.  I didn't get the sense she'd stayed in Brockton Bay these past few months.



Then she spoke, and my initial impressions were banished the instant I heard her hard tone.  ``Collins?  Thirty words or less, give me the rundown.''



The guard answered her, pointing to Emma, ``Extended argument was initiated by the blonde one.  The one with the glasses tried to back out.  Blonde escalated to pushing and shoving, I stepped in.''



``Okay,'' she said.  ``Witnesses, any commentary?  Keep it short.''



``What he said,'' the girl with the half-shaved head said, sullen.  ``The one who started it, I think her name was Emma?  Yeah.  Um.  She's a bitch.''



This was somehow surreal.  I wondered if I was caught in some kind of trap.  The Ambassadors didn't, to my knowledge, have anyone with a power that could mess with my head.  Maybe Haven or the Fallen had someone like that, capable of trapping me in some kind of warped world where things actually turned out \emph{okay}, leaving me in a state where I never wanted to leave.



Such a world wouldn't necessarily have Emma in it in the first place, though.  Or Greg.



``Emma didn't do anything wrong,'' the blonde in the purple shirt said.  ``There's a history.  She was only responding to some stuff that happened before.''



``I don't care about what happened before,'' the principal said.  ``I care about keeping the peace.  We've already had three fights \emph{with weapons}, and the day isn't even half over.  No less than ten fistfights.  Nearly a third of the students attending this school were in Brockton Bay during the recent crises.  Some were Merchants, others were members of the white supremacy groups, and many more either found or \emph{are still taking} refuge in a territory held by the current crime lords of Brockton Bay.  Friction is inevitable, I'm certain many of my students have post traumatic stress disorder, and any number of students haven't yet made the transition from being a survivor to being an ordinary student.''



She leaned her elbows on the desk.



``That's fine.  I'm willing to accept trouble as a fact of life, given recent events.  It would be unfair to hold you-'' she paused to eye me, the girl with the hair and the boy in the sleeveless t-shirt, ``-to the same standards as any other student, given what you've been through.''



``That's not fair,'' Emma said.



``Emma,'' the principal said, ``What you did was monumentally stupid and dangerous.''



Again, that surreal feeling.  This would be the point that I woke up to find I was still buried in Echidna, experiencing some warped reflection of past events, only in a more pleasant vein.  Or maybe this scene twisted around and I'd realize I was in some modified agnosia fog and everyone around me was a member of the Nine.



Principal Howell continued, ``You there, your name?''



``Terry,'' the boy in the sleeveless t-shirt said.



``Did you bring a weapon to school today?''



``No.''



``Have you been in a fight, in the last few weeks?''



``A few.''



``Okay.  And you, miss?''



``Sheila, and yeah.  Brought a weapon.''



``Do you have it on you?''



Sheila reached into a back pocket and withdrew a keychain.  A piece of metal dangled from the end, a bar that could be gripped, and two spikes that stuck out in front.  It was like brass knuckles, but not quite.  The same principle applied.



``Thank you.  If you could hand them to Collins, I'd appreciate it.''



Sheila gave Collins a wary look.



``Or you could step outside,'' Howell suggested.



``Yeah,'' Sheila replied. ``I'll do that.''



She turned on her heel and stepped out of the office.



``And you?  Your name?''



She was looking at me.  I responded, ``Taylor Hebert.''



``Were you armed?''



``Yeah,'' I said.



``She handed over her weapon without a fuss,'' Collins said.  ``Cheap knife, basic sheath.''



``And, if pushed, if you'd had it, would you have used it?'' the principal asked.



I hesitated.



``You won't get in trouble if you say yes.  Be honest.''



``I don't know,'' I said.  ``Define `pushed'.''



``Nevermind.  \emph{Have} you used it?''



``That one?  No.''



``But you have used \emph{a} knife?''



I nodded, reluctant.  I couldn't shake the feeling that the walls were going to close in around me, screwing me over.



``I hope you're getting my point,'' the woman said, turning back to Emma.



``You're saying they could have hurt me,'' Emma replied, sullen.



``\emph{Would} have, in some cases.  This isn't the city you're used to, nor the same students.''



``It's fine,'' Emma said.



``We'll see.  Just putting you into the computer.  Emma\ldots what was it?''



``Barnes,'' I supplied.  ``E-S at the end.''



She typed on the computer keyboard to her right.  ``And Taylor\ldots Hubert?''



``Hebert.  E-B-E.''



More typing.  ``Hebert.  Just give me a second to pull records\ldots damn.  Fancy new school, you'd think they'd give us better equipment.''



She hit the power button.  The computer took a minute to reboot.



Long seconds passed.  Nobody spoke.



The screen flared back to life.



``Hm,'' she murmured.



``What is it?'' Collins asked.



``A number of past incidents.  And we got the emails from Winslow High School, I did a search for their names, and there's one that post-dates the Endbringer attack.  It's apparently a series of text messages between an Emma Barnes and Sophia Hess.  There's a great deal of discussion of the ongoing bullying campaign against Taylor here.''



I glanced at Emma.  She'd gone pale.



\emph{A final `fuck-you' from Sophia?  Guess she wasn't a friend after all}.



The principal looked me square in the eye.  ``Would you like to press charges?''



I couldn't even think straight, hearing that, it was so out of tune with my expectations.



No.  I was still seated on the hard plastic chair, Emma to my immediate left.  This was reality.



This was everything I'd wanted, as far as the Emma situation: to enjoy a small victory, to see her house of cards come tumbling down.  To actually get to press charges?  To see justice?



``No,'' I said.  Emma's head snapped to face my direction with enough speed that I thought she might have given herself whiplash.



``Why not?''  Principal Howell asked.



\emph{Because I'm a supervillain, and I don't want the scrutiny.  Because her dad's a lawyer with connections, and it won't work\ldots}



``Because she's not worth the trouble,'' I gave her the first answer that I could think of that wouldn't cause any more problems.  \emph{Time spent on this is time I can't devote to my territory.  I don't want more conflict}.  \emph{Not with all the other issues surrounding this.}



``The school can take action against her without your consent,'' she said.



``Feel free.  I want to be done with her, that's all.''



``Very well.  Emma?  I'll see you again in September.''



``September?''



``The summer classes we're offering are very much a privilege.  Now, I'm sure you've faced your share of stresses in having to relocate twice in a short span of time, but I'm not inclined to extend the same leniency to you that I'm extending to those who've been through so much more.''



I suspected Emma was at least as stunned as I was.



``When you return, we can discuss whether you'll repeat the tenth grade, and whether you'll repeat it \emph{here}.  I'll have had time to review the emails and past records\ldots''



She tapped a few keys on the keyboard, then frowned.  ``\ldotsWhat was I saying?  Right.  Given the possibility that Taylor might choose to attend in the future, and even just the basics I'm reading here, it may not be conscionable to let you attend as well.''



``This is ridiculous.  My dad's a lawyer.  There's no way he'll let this happen.''



``Then I expect we'll have a great many discussions in the future.  Collins?  Would you please take her to the front?  I'd like a word with Ms. Hebert.''



``Will do.''



Maybe not a delusion.  A trap?  Head games from Accord?  Or was she an Ambassador, trying to curry favor?  I wasn't sure what every member of the Fallen or the Teeth could do.  Could one be a shapeshifter?  Something else?



The door shut behind Collins, leaving the principal and I alone in the room.



``Satisfactory?'' she asked me.



``What?''



``Is this end result satisfactory?  If you were holding back because you were afraid your membership among the Undersiders might come to light, rest assured I can be discreet.''



She \emph{did} know something.



``I- I'm not sure I understand.''



``It doesn't matter.  I got the impression you didn't want to be treated any differently.''



``Who \emph{are} you?''



``A vice principal in well over her head,'' she said, leaning back in her chair.  ``I didn't see it firsthand, but I've felt the effects of this\ldots long series of disasters.  My predecessor made it through, past an Endbringer attack, past food shortages and disease, past the roving gangs, the thugs and looters, past the Slaughterhouse Nine, an amnesia fog and a takeover of the city.  So many things.  And at the end of it all, just when things started to get better, he couldn't adjust.  He got in a fight, was punched in the head, and died soon after of an embolism.''



``I'm sorry.''



``Seventeen years working together.  He was like a brother.  I told myself I would keep the peace.  Someone gave me a list of names, and I recognized your name on that list.  So perhaps I support certain students and keep an eye on the ones who would inevitably cause trouble anyways.''



\emph{Tattletale.  She arranged this}.



``I'm not confirming or denying that I am such a student-''



``Of course.''



``-but why?  What do you get out of it?''



``Peace.  It's an ugly road to travel to get there, but it's peace.  I lost one good friend and boss to the crises here, I won't lose anyone else.  \emph{Particularly} not my students.''



Why did she have to tell me?  I would have been content to be ignorant here.  This was a perversion of justice.  The fact that it was perverted in my favor didn't matter.



``Treat me like you would anyone else,'' I said.



``I will.''



I couldn't quite believe her.  If she was currying favor with Tattletale, helping to solidify Tattletale's hold and perhaps feeding Tattletale information on more troublesome gang members, I wasn't sure I could trust her to stay impartial here.



I'd won, so to speak, but this small revelation had taken the justice out of it.



``I'm going to go,'' I said.



``I need you to fill out some paperwork, so everything's organized for Emma's suspension.  Are you a student?''



``No.''



``Are you \emph{intending} to be a student?''



``No.''



``Okay.  Then I'll have you fill out a form as a visitor.  Let me reboot my system again, print what you need, you can fill out one short page, and I'll manage the rest.''



I was about to protest, to give some excuse and go, but the phone rang.  She picked up and pressed one hand over the mouthpiece.  ``Wait at the front, a secretary will bring it to you.''



I couldn't refuse without intruding on the conversation.  I stepped outside.



Emma was at the front, too, slouched in a chair with Collins standing beside her.  No doubt she'd had a secretary let her call her dad, or would as soon as the opportunity came up.



I stood at the opposite end of the room.



I felt numb.  A little disgusted with how things had turned out, that the only reason this system seemed to be \emph{working} was because it was already corrupt to a fundamental level.  I could still feel some of the anger and irritation from the argument with Emma, the thrill of adrenaline\ldots



I raised a hand to adjust my glasses and found my fingers were shaking.  I was trembling, and I couldn't identify why.  None of the emotions I could single out would account for this kind of response.  Even all put together, they shouldn't have gotten me halfway here.



I had a lump in my throat, and I felt like I might cry, and I wasn't \emph{sad}.  Was I happy?  Scared?  Relieved?  I couldn't sort anything out in the jumble.



Was my emotional makeup \emph{that} fucked up?



I found a chair and fell into it, rather than sitting.  I focused on deep breaths, on using my power to contact my bugs and detach myself from things.



``Hebert?  Taylor Hebert?''  A secretary was calling out for me.



I stood and made my way to the front, where I got the paper, already attached to a clipboard.



Some had already been automatically filled in, and there was a header asking me to double-check the details.  My name, my age and grade, the address\ldots



I stopped.



Address:  911 Incoming St.
Alt Address: 9191 Escape Ave.



I looked up in the direction of the principal's office.  She was standing at the window, staring at me, a phone pressed to her ear.



She mouthed a word at me.  `Run'.



\emph{Someone knows I'm Skitter}.



I ran.





