





From the moment Charlotte had sent her text, I'd been bracing myself for the worst case scenario.  I'd resolved the situation with Greg, and I'd had just enough time to let my guard down before things started falling apart \emph{for real.}



A guard stopped me in my tracks before I was three steps out of the office, arresting me mid-stride by setting his hands on my shoulders.



I resisted the urge to fight him.  I wasn't sure I \emph{could}, without a weapon, my armor or powers, and it threatened to make the situation worse.  He peered down at me, but I averted my eyes, staring down at the ground so he couldn't get a straight look at my face.



``No running, kid,'' he said.



He let me go, and I resisted the urge to breathe a sigh of relief.



My thoughts were a mess, a jumble of half-finished thoughts, ten times worse than it had been earlier in the day.  Somehow, in the midst of it, I managed to establish a few priorities.  Slip out, get rid of evidence, assess the threat, and then \emph{address }it.



I walked slower.  I had the papers I'd removed from the clipboard, and I started tearing them up as soon as the guard had disappeared through the doors of the office.



On a more strategic level, I drew on a share of the handful of bugs in the school to get a sense of my surroundings.  I'd be letting people know Skitter was present, if they noticed the odd movements of the flies and ants, but I had good reason to believe someone already knew.



Either the people after me were the good guys, and it didn't matter if I clued them in, or it was one of my \emph{other} enemies, and the heroes showing up could be a \emph{good} thing.



Arcadia High consisted of two longer buildings joined by a third, joining them to form something like a capital `H'.  The main office, where I was, and all the other administrative and staff-related facilities seemed to be located around the center.  The only exits from this immediate area would open into an open space where I would be surrounded by walls lined with windows, all looking down at me.  Worse, the doors all had the heavy horizontal bars that suggested they were emergency exits, and an alarm would sound if I used them.



Assuming I had someone after me, I couldn't afford to put myself in that position.



That left me two options.  I could head into the building to my left, which featured four stories of classrooms, the cafeteria and a gymnasium, with a door that led to the student parking lot at the front of the school, or I could head right, into a building that was much the same, though longer, with an auditorium and the front doors of the school in close proximity to one another, and quite a few more classrooms.



I headed for the front door, to my right, depositing the scraps of paper in a trashcan on my way.  I moved as fast as I could without drawing undue attention, discreetly placing bugs on all of the guards I could find.



I stopped in my tracks as my bugs made contact with two \emph{other} individuals.  Adamant and Sere were in the company of two guards, moving from the front door to the intersection immediately in front of me.



Making a sharp right, I headed for the stairwell, ducking away before they could advance far enough ahead to get a glimpse of me.  I'd worried they were making a beeline straight for me, but they stopped at the junction where the two hallways met.  I was already reaching the hallway below.  The guidance counselor's office and staff meeting rooms sat behind floor-to-ceiling windows with the same glass that the exterior windows had: hexagon-shaped cells blending near-seamlessly into one another.  Looking straight at it, I couldn't tell the difference, but the light caught each cell differently if I viewed it at certain angles, making them stand out.  Measures against Shatterbird?



Behind one of the windows, I could see two guidance counsellors sitting in a circle with a dozen students.  Nobody, not even the guard who was standing on the other side of the glass door, gave me more than a glance.



The exterior windows of the building were all securely closed.  The building was cool despite being a greenhouse of sorts, but it made getting my bugs into the building a difficult matter, and that left me with a relatively small swarm.  I gauged the number of bugs I could spare, and situated the less mobile bugs on doors and at the points where the walls met the floor or ceiling.  I might have preferred a denser collection, to map out my surroundings, but it gave me a sketchy mental picture of how the hallways were laid out.



A small cloud of flies was only now reaching the front office, slipping inside as a student opened the door, navigating between legs and feet to make their way to the principal's office.



Listening in required conscious thought, but I'd been working on training my brain to follow human speech with the insects' alien hearing.  It was easier, the more I had nearby, but I'd have to make do.



``\ldots{}fight on my campus\ldots'' she spoke into the phone.



I had some information now, for as long as she was on the phone.  Not much, and it required me to divert some focus to translating, but it was something.



``\ldots{}of my students are \ldots{}ly sensitive \ldots to \ldots them feel unsafe\ldots''



It was an unfamiliar school, and while I had a basic sense of the layout, particularly on the exterior, the interior was something of a hurdle.  The hallway I was on ended in short staircases at either end, each of which led up to the main hallways of the larger buildings.  I made my way towards the one furthest from Sere and Adamant.



``\ldots{}if that's an order\ldots yes\ldots fine\ldots''



The principal hung up the phone, placing it on her desk.  She didn't act right away.  I quickened my pace.



The bugs I had on her pant legs informed me that she was swiveling around.  I had to think about the layout of her office before it clicked.  The computer.



I was at the top of the stairs, the door that led to the parking lot at my left, when the signal went through.  Every single guard in the building reacted in the same moment, as did Adamant and Sere.  Some withdrew things from their pockets -phones, I could guess-, while others were already kicking into action.



It wasn't just the guards.  The bugs I had on classroom doors informed me of some students slipping out of class.  Two students, both boys.



My enemy was the Protectorate, or someone with strong connections in the Protectorate.  Nobody else would be able to pull this.



Guards stepped into the building and shut the doors behind them.  The heavy, mechanical sound of the doors locking echoed down the hall around me; the doors leading outside were all being sealed shut.



The gate at the front of the school was closed, and a guard was heading for the chain-link barrier at the edge of the parking lot as well.



Could I run?  Maybe.  Fight my way past the guards?  It was possible.  I could cloak myself in bugs, use my limited repertoire to disguise myself, to disable and/or distract them while fighting my way outside.  Could I get to the end of the parking lot in time?  That, too, wasn't impossible.



All together?  With barely a hundred bugs available?  I wasn't so sure.  Any fight took time, it involved a risk to myself, and I wasn't wearing my costume.  If any of the guards had a weapon they'd confiscated or if one of the capes in the area caught up with me, I'd be more than screwed.



I didn't have any bugs on my person.  I'd been concerned about a pat-down at the gate, and I didn't want to have bugs crawling throughout the inside of my pant leg or in my pockets when a guard searched me for weapons.  I wasn't wearing my costume for much the same reason.  Stupid of me.



I was stuck.



``\emph{May I have your attention please?}''  Principal Howell's voice sounded from speakers throughout the school.  ``\emph{The school is now being locked down.  For your own safety, please remain in your classrooms.  Students not in an assigned classroom should proceed in a calm and orderly fashion to the nearest seating area.  Students in the north wing of the school will need to make their way to the auditorium.  Students in the south wing should gather in the cafeteria.  Remain calm and rest assured: there is no immediate danger.}``



The noose was constricting around me.  The students would be contained in select areas, and classrooms would be cleared one by one.  If the Protectorate was involved, I wasn't even sure I could find a proper hiding spot.  Didn't Kid Win have some ability to see through walls or detect heat signatures with his goggles?



The two boys had reached a room on the bottom floor, near the gymnasium, and were quickly changing into their costumes.  Clockblocker and Kid Win.



What did the good guys know?  They'd been alerted that I was in the school.  I'd been in the office only minutes ago, and the principal had put my name into the computer.  That was probably the catalyst, given how fast things had proceeded in the minutes since.  The principal got the phone call, and had ordered the lockdown as a consequence.  The fact that she'd warned me, it didn't jibe with the lockdown: she probably hadn't wanted to do it.



It struck me that they didn't know that I was in the school \emph{now}.



Inside of the building, I was largely defenseless.  Outside, I did have my bugs.  I doubted I could get out without drawing attention, but I \emph{could} theoretically get them to call off the lockdown.



My bugs moved from the surrounding blocks and collected near one of the fire doors I'd noted earlier.  They formed into a decoy, a rough copy of my general silhouette, covered in bugs, and then began moving toward the school gates.



One of the guards standing by the auditorium saw and shouted for Sere.  The white-shrouded hero hurried for the door.



Sere was a long ranged cape, probably capable of killing my swarm with little difficulty.  I split my swarm off into further copies, maintaining their movement towards the gate and the walls.



Another announcement was broadcast throughout the school.  ``\emph{A supervillain is currently near the school entrance.  Students in the central areas of the school should relocate to the cafeteria.  Anyone already in a secure place should please remain where they are.}''



The office was emptying, now, and guards were breaking away from their groups to ensure that every student that had been sitting around in the hallways was moving to the appropriate areas.  Emma was among the forty or fifty students heading toward the cafeteria, nestled in the midst of the group, while the principal followed at the rear with two guards in her company.



Behind me, the guidance office was evacuating as well.  The glass door opened, and the soundproof seal broke.  I could hear one of the counselors speaking to the twelve or so teenagers around him.  ``Let's go to the cafeteria.  If this takes a while, we'll at least be able to eat.''



He spotted me and gestured for me to join the group.



I could have argued and asked to go to the auditorium instead.  There were any number of excuses that could have worked, including `I have an issue with one of the students who's in the cafeteria'.



But I was more interested in being invisible.  Better to play along, to think of a plan and execute it, while doing as little as possible to draw attention to myself.  Here, at least, I'd be hidden among others.  I joined the crowd moving in the direction of the cafeteria.



More guards were directing other students to the cafeteria, the groups merging into a single mass, with the cafeteria doors as the bottleneck.  Inside, everyone was spreading out to find tables.  Again, I noted the distinction between the two varieties of student.  The bright and cheerful ones were collecting together, filling up every space at the tables closest to the door and to the front of the cafeteria, where all of the food was available.  Others were spreading out, alone or in groups of two to five.



The principal and other staff members were standing by the door, seeing that everyone filed peacefully into the room.  Emma was sitting at one table with all of the secretaries and a few of the teachers who I supposed hadn't had a class to teach.  She glared at me as I walked into the room.



I found Charlotte, too, identifying her by the cube of paper with the ladybug inside that I had my more prominent minions carrying these days.



``Taylor!'' she hissed, as I made my way towards a table at the back of the room.



I was dimly aware of Sere striking down one of the decoys.  The moisture in the air zipped to his hand, and nearly half of the decoy was ruined, the bugs dazed or unable to move.



The spiders, I noted, suffered worse than most.  They used a kind of biological hydraulic system to move.  Shit.  I liked my spiders.  They were particularly useful.



I reached Charlotte and murmured, ``Best if you don't know me.''



``Hey, Taylor,'' she hissed the words, twisting around in her seat.  When I didn't reply, she repeated herself, ``\emph{Hey}.  Is this about you?''



``I think so,'' I muttered.



I took a seat at a table near the back, folding my arms in front of me and resting my chin on the back of my hands.  Staying out of sight, while keeping an eye on everything.  It also allowed me to focus on my swarm.



My bugs were discreetly tracing back routes and other options.  Was there a place where the cafeteria staff unloaded the day's food?  Some back way leading from, say, a gym or custodial entrance?  A way onto the roof, even?  I didn't have enough bugs to spare that I could leave them on walls.  I was forced to personally memorize every corridor and feature of the building that might be important.



Outside, Sere was working at destroying my decoys.  I split off more copies, and then moved one group to him to see if I could blind him.



The bugs were being sucked dry of moisture as they got too close to Sere; I wouldn't be able to disable him with just my swarm.  He drew more water from a cloud of bugs, desiccating and killing hundreds.



The number that died was indicative of something, though.  As devastating as the attack was, the effect didn't cover a massive area.  It was a roughly cone-shaped area, with a long reach, but narrow breadth.



If he was surrounded by moisture, maybe I could use that against him?  My flying bugs started doing bombing runs.  They picked up small stones and dirt, using the fine tarsals that helped them cling to walls.  There wasn't the suction, but it served to allow them to pick up specks at a time.  They flew in tight loops, staying high over Sere as they dropped the fragments, touched ground to collect more dirt, and repeated the process.  I was careful to spread them out and collect the fragments from multiple places so he couldn't kill too many at a time.



Dense moisture and dirt could become a thin mud, and it might serve to blind him or distract him where my bugs couldn't.



In the cafeteria, another group of students was filing inside.  Fifty or sixty in all, they each bore telltale signs of the kids who'd stayed.  Many were drenched in sweat, and the teacher with them held a basketball.  Had they been in the gym, burning off nervous energy, working on building social bonds and all that?



There were maybe three or four hundred people in the cafeteria, now, as students from all over the school streamed in, including most of the ones from the auditorium.  With the increasing number of students, it was impossible for anyone to have a table to themselves.  A group of three boys claimed the far end of Charlotte's table, and she stood up.



She had issues around unfamiliar men.  It might have served as a push for her to do what she'd been debating doing anyways.  She joined me at my table, sitting close enough that our shoulders touched.



``What's going on?'' she whispered.



``You know when Tattletale vetted everybody?''  I whispered back.



Charlotte nodded.



``She made a list of names, some vetted people along with some others who were safe.  Mixing it up.  She gave the list to the principal, with the idea that maybe she could cut us some slack and we'd help keep the peace in the school in exchange.  So she had an idea that I was related to the Undersiders, she told me to run and hinted someone might be after me,'' I said.



Charlotte nodded again, mute.



``I tried,'' I whispered, ``but I couldn't cover enough ground in time.  Someone forced her hand and ordered her to put the school on lockdown.  I can't slip out without drawing attention to myself, I'm not in a position to fight, and it's only a matter of time before they find me.''



``\emph{Shit},'' she said.



``Exactly,'' I said.  ``I won't blame you if you want to move somewhere else.''



``I'll stay,'' she said.



``Char--''



``I'll stay,'' she repeated.



I relented.  I couldn't afford to focus on this, when I needed to control my bugs and memorize any possible escape routes or hiding places.  ``If anything happens, get clear.  You don't know me.  Your `little brother' is counting on you, and he should be your priority.''



``Little brother?'' she asked.  I saw the realization as she remembered our code word.  `Little brother' referred to all the kids in her charge.



``Oh.  Right,'' she said.



Kid Win was making a beeline for the front door.  I clustered bugs on the surface of the door, blocking his line of sight as much as I was able.



It didn't work.  \emph{The thermal goggles}.  \emph{Which means he can tell there's no body inside any of the decoys}.  He pushed the door open and shouted, ``Sere!''



That was about as far as he got before my bugs descended on him, filling his open mouth.



``What are you going to do?'' Charlotte asked.  With the degree of attention that I was devoting to what was going on, she sounded almost distant.



Even with the murmuring of hundreds or so students conversing, the cafeteria was eerily still and quiet compared to what was going on outside.  Adamant was standing at the doorway to the auditorium, simultaneously trying to keep an eye on the stray students from the north building and the fighting outside.  Clockblocker was making his way to the front.  He was slightly different; he wore what seemed to be a gauntlet, out of proportion with the rest of his body.



``I have a few options,'' I whispered my response.  ``I could be aggressive, take on the people at the door.  I think I could slip away.''



``Why didn't you do that already?''



``They were too guarded, and they were anticipating trouble from \emph{within} the building.  My bugs are causing some chaos outside, now, and they'll have their backs turned.  I'll have time to improvise a mask, which I didn't, before.''



``You have to get out of the cafeteria first.''



``I'm not too worried about that,'' I said.  ``There's two or three possible escape routes I've been able to find, if I can get my hands on a set of keys or create a big enough distraction to get away with making some noise.  The principal has my back, and she might make it easier.  I'd ask her for a key, but I'm not sure she would be willing to risk it, and there's too many people around her.''



\emph{Including Emma}, I noted.  One person I could count on to pay attention to me.



``What if she's the one who made the call to these people who are after you?''



\emph{The principal?}  I shook my head.  ``Her priority is keeping this school and its students safe.  Besides, I overheard her communicating with someone on the phone.  If she was playing both sides, there'd be no reason for her to maintain the ruse when I wasn't anywhere nearby.''



``Unless she knew you could hear through your bugs,'' Charlotte added.



``Unless she knows,'' I echoed her.  ``I don't think she does.''



Kid Win was suffering at the hands of my swarm.  He drew a weapon, but my swarm was already prepared with lengths of silk.  They constricted the weapon and prevented it from unfolding.  Sere, for his part, had his hands full trying to take down the decoys.  A large part of what I was concentrating on was the decoys, getting enough details right, and splitting them off in a way that suggested I \emph{could} be any of them, while simultaneously keeping them far enough apart that he couldn't attack more than one at once.



``Taylor,'' Charlotte whispered.  ``If they know who you are, they \emph{know}.  They could find you again, or put your face on the news.''



``If they did, it would be breaking a good few unwritten rules.  \emph{Especially} if they only knew who I was because I helped with the Echidna situation.  They can't afford to punish villains for helping against the big threats.  It would mean fewer people showed, and they need all the help they can get.  Here, at least, they could say I was intruding on neutral ground.''



The explanation felt feeble.



``It doesn't make sense,'' Charlotte whispered, echoing my line of thinking.  ``Doing it here\emph{, at a school, }with so many potential hostages around.  Breaking the code?''



``I'm thinking\ldots'' I replied, ``I'm thinking everyone knows the Protectorate is falling apart.  Legend's gone, Eidolon's announced he's leaving as soon as things get quieter, the head of the PRT stepped down, a whole bunch of rank and file members left, and so did Weld and a lot of the more monstrous capes.  Maybe there's pressure from the top to put one in the win column, remind people why the Protectorate exists.''



\emph{And who better to take down than the creepy teenage supervillain who's leading the team that took over a city?}



``But in a \emph{school}?''



I didn't have any guesses to offer on that count.  I focused on the fighting outside instead of responding.



Getting too close to Sere was killing my bugs just as easily as his long ranged absorption attack.  I had to attack him from range, and the rain of dirt and small stones wasn't doing anything, as far as I could tell.



I turned to a tactic that had crossed my mind while fighting Echidna.  She, like Sere, had been tricky to get close to.  Unlike Sere, she'd been too big to really tie up.



Spiders drew out lines of silk and formed them into cords, weaving them into one another to form extended lines, fifty or so feet long.  With the combined efforts of dozens of flying insects, half gripping one end and half gripping the other, the lines were flown in Sere's direction, so he was caught by the middle.



The bugs holding the ends then continued onward, keeping the cord taut as they circled him, one group flying clockwise, the other flying in the opposite direction.  In this manner, they orbited him, winding him up in a single length of cord.



With five cords being wound around him in that fashion, I soon had him hampered, his arms and legs restricted in movement.



He kept moving forward, attacking my decoys.  As he passed a signpost, I hurried to have my bugs wind the remaining lengths of cord around it.  Lines went taut, cords constricted around him, and he fell.  He struggled, but it didn't seem he would be on his feet anytime soon.



With Kid Win on the ground, thrashing, that was two down.



The other two, I was pretty sure I could deal with them if it came down to it.  I wasn't sure what Clockblocker's glove did, but I had a suspicion.  Adamant's armor was just begging to have silk cords wind through the chain links and armor plates.



My bugs rifled through Kid Win's pouches and armor compartments.  Masses of bugs and teams of the larger, stronger bugs working to pull silk cords helped to divest him of various tinker tools and components.  His smart phone, a cylinder with a trigger on the front and a button on top, a sphere with a hole through the center, with screw-like rifling and electrical connectors in the interior.  There were two devices like tuning forks, too, with tines that wound around one another without touching, and wires beneath the handles.  Bugs in his ears helped to work an ear bud out of position and carry it off.



Once he was denied as many of his tools as I could move, I dragged them away.  It was only when I was sure that he wouldn't be able to use them against the swarm or against me that I eased up on him.  I let my bugs drift in the general direction my decoys had gone, as though I were leaving or gone.



He stood, gagging and choking.  Sere wasn't in sight, and I'd taken Kid Win's phone.  There was only one place for him to go if he wanted to communicate with the others and touch base.  He headed back into the school.



I was ready.  Bugs flowed out of his pockets, gaps in his armor and from where they'd clustered at the small of his back.  I tied his wrist to the door handle.



It took him a long few seconds to realize the door wouldn't swing shut until he moved.  That bought the remainder of my swarm time to turn around and flow through the open entryway.  They headed straight for the guards, and swept into their pockets the same way they had with Kid Win's pouches.



Keys?  Yes.



While Kid Win and the guards were blinded, my bugs fetched the keys.



I stood from the bench of the lunch table.  ``I think I'm set.''



``Just like that?'' Charlotte asked.



I looked at the front of the room, where other students were feeling hunger and teenage appetites overcoming their fear of what was going on elsewhere in the school.  Only a dozen or so.  \emph{Maybe they don't have a steady supply of food where they are}, I mused.  There \emph{were} areas of town which weren't in good shape.



\emph{There're pizza slices}, I noted.  It was a reminder of how the day wasn't going as I'd planned.



``It shouldn't be a problem,'' I said.  \emph{Get out, then see what Tattletale can manage as far as damage control}.  ``Wish me luck.  I'll send you a message and meet you at the lair after school if everything goes according to plan.''



I crossed the cafeteria, heading for the buffet tables and sneezeguard-protected counters with empty trays waiting to be filled by staff.  Emma was at her table, I noted, surrounded by secretaries and teachers.  I was joined by other hungry students, eager for their free food, and their bodies helped to block me from the sight of both Emma and the staff.



\emph{Confidence}, I thought.  I stepped around the counter and through the doors that led into the kitchen.  Confidence made it look like I knew what I was doing; being furtive would only arouse suspicion.  My bugs were still carrying the keys, bringing them along an air vent.  I'd need to find a way to open a vent cover and retrieve them, but it was among the smallest of the problems I'd face today.



I found a door to the outside.  My bugs clustered on the other side, my hand pressing against my own, separated by an inch and a half of door.  I glanced over my shoulder to make sure I hadn't been followed, then started looking for a way into the air conditioning duct.



\emph{The smallest of the problems I'd face today}.



There was an impact, heavy enough that the lights flickered.  Even the bugs I'd gathered on the door were knocked loose, both by the force of the landing and the flying dust and debris.



Right outside the door.



I didn't need to move my bugs to search out the identity of \emph{this} antagonist.



A figure strode through the swarm of bugs.   He tapped the door with the end of his weapon, and the breath was knocked out of me.  Every bug within thirty feet of the door died, including the ones in the air conditioning duct.



I was still reeling as he pushed against the door.  It was deadbolted, but the metal of the door's surface buckled, and it tore free of the frame.



He was wearing armor, forest green and gold, with the stylings of a lizard's frills or bat wings on the trim, and a faint etching of scales to the green portions.  His spear, too, bore a distinctive design, with an etching like a lizard's skull worked into the heavy spearhead.



He advanced, his spear point leveled at my chest, and I backed up, maintaining a distance between us.  To do otherwise would mean letting him drive the weapon into my chest.



On the other side of the campus, another heavy armored suit touched ground, somewhat more gently.



He stopped when we were at the front of the cafeteria.  I kept backing up, knowing it was futile.  Dragon had exited the other suit, and was using a jetpack to navigate the hallway, flying towards us with an accuracy and ease of movement that belied how fast she was moving.



I didn't have an escape route.  The woman stopped directly behind me, at the entrance to the cafeteria.



``Dragon,'' I said.  ``And Armsmaster.''



``The name is Defiant,'' Armsmaster corrected me.  His voice had a funny sound to it.



``Skitter,'' Dragon answered me, loud enough for everyone to hear.  \emph{Her} voice was almost gentle.  ``I'm sorry it worked out this way.  My hand was forced.''





