





The appearance of the heroine in gleaming power armor had brought the room to a hush.  The silence only allowed Dragon's words to carry, bouncing off the hard floor, reaching the assembled students and staff of Arcadia High.



A low murmur ran through the room like an almost imperceptible aftershock, informing anyone and everyone who hadn't been in earshot.



I could see Emma too, or I could see glimpses of her, between the students that were backing away from the front of the room.  Already pale in complexion, she was \emph{white}, now, staring.



I exhaled slowly, though my heart was pounding as if I'd just finished a hard run.



Defiant advanced a step, with the door to the kitchens behind him, while I took a few steps back toward the rest of the cafeteria, putting both Dragon and Defiant in front of me.  Some of my bugs flowed in through the gaps around the door he'd rammed through.  He'd slammed it shut behind him, but the metal had twisted around the lock, giving smaller bugs a path.



He slammed his spear against the ground.  The entire cafeteria flinched at the crackle of electricity that ripped through the air around him, flowing along exposed pipe and the heating ducts in a path to the door.  Every bug in the hallway died.



No use bringing bugs in that way.



I looked around me.  This wasn't an optimal battlefield.  There were counters all around me, limiting my mobility, while barely impacting theirs.  Someone had signaled Kid Win, Clockblocker and Adamant.  The three heroes were heading our way.  Sere remained tied up outside.



Five capes against me.  With the bugs that had flowed into the building with Kid Win, I had maybe a thousand flying insects and some spiders.  Not nearly enough to mount an offensive.  I had neither a weapon nor swarm to give me an edge.  I didn't have my costume, either, but that wasn't liable to matter.



Once upon a time, I'd had trouble getting my head around what Grue had been saying about reputation, about image and conveying the right impressions.  Now it was all I had.



I let out another slow breath.  \emph{Calm down.  }I rolled my shoulders, letting the kinks out.  There was something almost relieving about the idea that things couldn't get much worse than they were right now.  \emph{Let the tension drain out}.  If they decided to drag me off to jail or the Birdcage, there wasn't anything I could do about it.



They weren't attacking.  Maybe it wasn't as bad as I thought.  Were they not here to arrest me, or were they covering major routes my bugs might travel, to minimize my offensive strength?



Or did I have leverage I wasn't accounting for?



I backed up until I'd reached a counter, then hopped up onto the edge, tucking one leg under me.  It was a vantage point that gave me the ability to look directly at Dragon, with Defiant at the far left of my field of vision and many of the students to my right, Emma included.



``Low blow, Dragon,'' I said, finally.  ``Outing me?  I thought you were better than that.''



Another murmur ran through the room, at what was essentially an admission.  Emma was frozen.  Her expression wasn't changing; eyes wide, lips pressed together.



``I try to be,'' Dragon replied.  ``I'm only following instructions.''



``I guess your bosses are a little annoyed at the armored suits my team trashed?  Are they demanding that you make up for it by dragging me into custody?''



Dragon shook her head.  ``Putting the armored suits up against you Undersiders was a beta test, and identifying major flaws is par for the course.  I do wish you hadn't melted down the Azazel\ldots It was expensive.  But that's not why we're here.''



``There are rules, Dragon,'' I said.  ``Expectations.  I fought Leviathan, I fought the Nine.  I was there for the fight against the Class-S threat downtown.  I don't want to sound arrogant, but I think maybe I deserve to, a little.  I've done my share.  You don't turn around and reveal my identity in front of a crowd.''



``It wasn't by choice.''



``You choose to follow \emph{them}.  It's not like twenty or thirty heroes haven't walked away from the Protectorate, recently.''



``It's not that simple, Skitter,'' Defiant said.



``It's \emph{never} simple.  But sometimes you have to take the hard road.  Sometimes you have to recognize that the people calling the shots don't know what they're doing.  Because \emph{this}?  Picking a fight in a school?  There's no way this makes sense.''



``The Protectorate is doing what they can to pick up the pieces,'' Dragon said.  ``Things are a little disorganized.  The best of us are working twice as hard, with half of the information, or \emph{incorrect} information.  If there are any errors in judgement on that front, I'd hope they're somewhat excusable, given circumstances.''



``Sure, but it's the rest of us who pay the price.  The last time we really talked, you were lecturing \emph{me} about priorities.  Do you really want to have this conversation?  Where I have words with \emph{you} about \emph{your} priorities, in light of everything that's happening with the Protectorate?''



I left the threat hang in the air.



``You won't,'' Dragon said.  She stepped closer, and I raised a hand, gesturing for her to stop.  I didn't really think about it.  She stopped where she was.



Why?  Why was she actually listening when I told her to stop?  If she'd advanced on me, grabbed me, there wasn't much I could do besides kick and scream.



When I didn't say anything, she added, ``It's not in you, Skitter.''



``You'd be surprised what I'm capable of,'' I said.  ``I've mutilated people.  Carved out a man's eyes, emasculated him.  I've chopped off a woman's toes.  Flayed people alive with the bites of thousands of insects.  Hell, what I did to Triumph\ldots he nearly died, choking on insects, the venom of a hundred bee stings making his throat close up.  Even Sere, outside at this very moment.  He's not very happy.''



Defiant and Dragon exchanged a glance.



``Your swarm shouldn't be able to get near him,'' Defiant said.



I shrugged.  \emph{Image, confidence, reputation}.  I hated myself for doing it, but I was thinking of Jack Slash.  He didn't wear a mask or a costume.  His power didn't make people shit their pants.  What he had was his \emph{presence}, an atmosphere of confidence.



Weeks or months ago, I might have had a hard time wearing that confidence the way Jack did.  The \emph{history}, the long sequence of events and conflicts where we'd come out ahead in our respective teams, it could just as easily be a burden, the accumulated weight of the various precedents we'd set, but we'd made it into our armor, something to make our enemies hesitate at a critical juncture.



``I'm guessing you're trying to contact Sere somehow,'' I said.  ``And it's not working.''



``Is he hurt?'' Dragon asked.



I didn't have to give a response.  Fear was a tool I could use, here, and I could achieve \emph{that} through uncertainty and the unknown.



I'd been thinking of Jack Slash before, but now I was thinking of Bakuda.  She'd been the first one to introduce me to that concept.



``You've got me thinking,'' I said, ignoring the question, ``Why set me up like this?  You two are too smart to put me in a desperate situation with this many hostages in arm's reach.''



``Is Sere hurt?'' Defiant growled the words.



``You put me in a room with three hundred people I could theoretically take hostage.  Why?  You can't be that confident I wouldn't hurt someone\ldots''



Emma was sitting to my right.  She hadn't budged from her position, safe in the midst of several of the school's staff.  I directed a centipede to crawl across her hand, and she shrieked.  In her haste to get up from the bench, she fell.  She scrambled to put distance between us.  Both Dragon and Defiant tensed.



I raised my hands in a placating gesture, assuring the heroes I wasn't taking it any further. ``\ldotsor you wouldn't be worrying about Sere right now.  You wouldn't have reacted like you just did.  Sere's fine, by the way, though I'm not saying he'll stay that way.''



Defiant relaxed a fraction.  I could see Adamant, Kid Win and Clockblocker entering the room behind Dragon.  She turned to say something I didn't catch, and both Adamant and Kid Win retreated.  They'd be going to find Sere, I could only assume.



I met Clockblocker's eyes, then looked to Dragon.  ``This is bait, isn't it?  You or the people who are calling the shots \emph{want} me to take hostages.  Because you have an answer handy, something that will stop me before they're put in any serious danger.  I take hostages to try to secure my release.  You\ldots I don't even know.  You gas us, or use some kind of controlled charge, like Defiant's bug zapper, and every bug in the room dies.  You get to be the heroes, I go into custody, and word gets around that the Undersiders aren't so benevolent.  The villains who own the city lose both their leader and the trust of the public, all at once.''



``It wasn't \emph{our} plan,'' Dragon said.  Her voice had a faint accent, just barely filtering through the sound filter of her mask.  ``I've studied your record.  I suspected it wouldn't work based on the decisions you've made to date.  Defiant agreed, though he based his judgement on your powers and versatility.''



``But you went ahead with it.''



``Orders,'' Dragon said, again.  ``And because we discussed the matter, and neither of us really believe you'll do any serious harm to any hostages.''



``You seem to be giving me a lot of credit, assuming I'll play nice.  And you seriously expect me to keep my mouth shut about all the dirty little secrets I've picked up on over the last few months, after you've played your last card and revealed my identity?  An identity you found out because I \emph{helped}?''



``That wasn't how I discovered it,'' Dragon said.  ``And you \emph{will} keep quiet, because you know how important it is.''



``Maybe,'' I answered her.  ``Maybe not.  If I'm going to die or going to jail anyways, why shouldn't I scream what I know to our audience, here?''



``Because you won't,'' Dragon said, ``And you can't.''



``Why don't we move this conversation somewhere else?'' Defiant asked.  He shifted his hold on his spear to a two-handed grip, threatening without being threatening.



``Out of earshot of all of these people?'' I asked, extending an arm in the direction of the gathered students.  ``I don't think so.  If nothing else, I'm entitled to a jury consisting of my peers.  I'll settle for you two taking a hit to your reputation if and when you attack or kill me.''



Which was why I was sitting on the counter.  I was less mobile, less able to get out of the way if they attacked, and that was a \emph{good} thing.  A detail that our audience wouldn't \emph{consciously} register, but they'd take something away from the fact that my opponents were being aggressive while I was so defenseless.



``We're not going to kill you,'' Dragon said.  ``We've been instructed to take you into custody.  I'm sorry we have to do it this way.  I'd hoped\ldots \emph{we'd }hoped to simply talk to you.''



``The both of you?  I wouldn't have thought Arm- \emph{Defiant} had anything to say to me.''



``We entered Brockton Bay's airspace, and I was informed that there's a major quarantine in effect here, relating to the portal downtown, and that the airspace is being strictly controlled.  We were forced to announce our reason for coming to Brockton Bay, and PRT members with higher clearance co-opted our mission.  We were ordered to confront you directly, \emph{here, }and to bring you into custody.''



``Why?'' I asked.  ``Those suits you deployed against my team were supposed to be used to hunt the Slaughterhouse Nine.  Either you've abandoned that chase, or you're about to tell me that there's something more important than stopping them.''



``That is something we can discuss while we are in transit,'' Defiant told me.



``Defiant-'' Dragon said, her tone a warning.



``I could say more here,'' he added, ``But there are too many prying ears.  If you were willing to move to a room nearby, I could explain.''



``No thanks,'' I said.



``You'd still have your power, and I know you can communicate with that power,'' Defiant said.  ``You're just as capable of communicating any secrets to them from elsewhere in the school.''



``If I moved somewhere out of sight and out of earshot,'' I said, ``My words wouldn't have the same dramatic effect.  Besides, I suspect our audience is the only thing that's ensuring that you play fair.  They have cameras, and you have reputations to uphold.''



``My reputation isn't a priority,'' he said.  Dragon nodded, but I wasn't sure if it was approval or agreement.



``You have your \emph{organization's} reputation to uphold.  For those of us who stuck around in Brockton Bay, we had reasons.  \emph{Something }kept us here.  There was something to protect, or people to support.  Some were just scared, because actually leaving was scarier than staying.  Others didn't have any place to go.  With the Protectorate slowly folding in on itself like a house of cards, I'm thinking \emph{you} had a reason to stay, a reason you're following orders you don't want to.  You're not about to rough up an unarmed, uncostumed girl and make them look bad on camera.  Not when you have that big a stake in things.''



Defiant glanced in the direction of the crowd.  A handful of students had cell phones out, watching the scene.



``Remind you of the hospital?'' I asked.  ``Similar scenario.''



``Yes,'' he replied.  He didn't elaborate.



``We could grab you,'' Clockblocker chimed in.  ``I can, or he can just walk up to you.  No violence necessary.''



``No,'' Defiant said.  Again, there was no elaboration.



It dawned on me.  Defiant and Dragon were playing it safe because they thought I might have a trick up my sleeve, like I had at the fundraiser.  I'd disabled Sere, despite the fact that he was supposed to counter my power, and I hadn't even made a big deal of it.  They knew what I'd done to Echidna, and several other events besides.



They were worried I'd pull something.



Defiant had a grasp on my powers, Dragon had a grasp on me as a person, and they'd gauged that I wasn't a risk to the others in the room.  Which, if I was being honest with myself, I wasn't.  They had the upper hand, they lost nothing by letting this play out, and so they weren't making a move.  They'd talk me down, so to speak, and if I did something, they'd use one of their gadgets or tricks to counter my play.



One of the worst possible things had just happened to me, with my secret identity becoming public knowledge, and here I was, unarmed without a single idea on how to get out of this\ldots and the good guys were playing it safe.  I smiled; I couldn't help it.



``Fuck me,'' Clockblocker muttered to Dragon.  I might not have made out his words if it weren't for the bugs I'd planted on the heroine.  ``It just sunk in.  It's really her.''



\emph{Why only just now}?



Adamant had distorted his metal armor to create a completely form-fitting metal suit, with only the thinnest possible slits for his eyes, before venturing outside.  He'd waded through my swarm, mostly blind, and he'd only just found Sere beyond the wall at the school's perimeter.  He reshaped an armor panel into a weapon to start cutting Sere free.



Could I have caught \emph{Adamant } too?  Probably.  But it wasn't worth the effort, not when he could reshape metal, with enhanced strength and durability on top of that.



Now that I understood what was going on, I felt like I had something of an edge.  Now, how could I leverage it?



``I'm sorry,'' Defiant said.



That threw my thoughts off track.  I tensed, but he wasn't apologizing for an imminent attack.  ``What?''



``In the past, when we've crossed paths, I should have made efforts to meet you halfway.  I didn't.  I've had time to reflect, I've had another person to talk to and give me some objectivity, and I've come to regret how things played out between us.  I could say more, but it would come out like excuses, and I doubt either of us want to hear those.''



``\emph{That's} what you came here to say?''



``In large part,'' Defiant said.



``We'd hoped to talk to you, one cape to another,'' Dragon elaborated, ``About the immediate future, with the Undersiders running this city, and \emph{your} expectations in particular, Skitter.  But both Defiant and I thought he needed to say something to you along those lines, and perhaps you needed to hear it.  If anything pushed us to come here, it was that.''



I didn't have a response to that.  It was easier when the opposition were assholes.  Expressing remorse?  How was I supposed to parse that?



Except, they'd done one thing that was assholish.  One incongruent element in all of this.



``One last question, then,'' I said.  ``Why?  Why out me in front of everyone?  It doesn't fit with the idea of Defiant being remorseful, it flies in the face of the unwritten rules, and I \emph{know} my team has played fast and loose with those rules, but I wouldn't expect you to break them like this, Dragon.  Not Defiant, either, if he's reinventing himself.''



Defiant and Dragon exchanged a look.



``What?'' I asked.



``It's better you don't know,'' Dragon said.



``What is?  And better for who?''



``Better for everyone involved,'' she said.



``Tell me.''



She glanced at Defiant, but he didn't turn her way.  ``A precog told us it was our best option for bringing you into custody.''



\emph{A precog}?  The incongruous elements fit together.  A plan of action that was riddled with little flaws and contradictions when seen from an outside perspective, that made sense when seen through the lens of someone who'd seen the future and worked out what criteria needed to be met to get the desired end result.  This, mobilizing on the school, it was the same kind of setup I might expect from a plan that Coil would have hashed together after a long question and answer session with Dinah, his `pet' precog.



\emph{Dinah}.



``Who was this precog?'' I asked, the question abrupt.



``Skitter-''  Dragon started.



``\emph{Who}?''



``You know who,'' Defiant told me.



It knocked the wind out of me in a way that I hadn't experienced with the revealing of my secret identity.  My blood ran cold, and all of my confidence just plummeted, as though it had fallen into a pit so deep I couldn't even see the bottom.



It was.  All of the lengths I'd gone to, the lines I'd crossed, to get Dinah away from Coil, to get her home to her family, and\ldots \emph{this}?



I was acutely aware of the crowd to my right.  They'd backed away from the front tables, and were clustered at the far end of the cafeteria.  Still, they'd be hanging on every word they could make out.  They were watching my every movement, every facet of this conversation.  There were cell phone cameras turned my way, and every second of footage would no doubt wind up on Parahumans Online or some video site.



I barely cared.  I felt a little numb as I swung my legs around to the far side of the counter and hopped down.  I wasn't standing as straight, and some of my hair had fallen down around my face, obscuring it.



``Did they force her to give up the information?'' I asked.  My voice sounded funny.  I couldn't pin down whether I felt angry, sad or any of that.  I had only the external clues, the way my voice had the faintest of tremors, and a strange hollow feeling inside.



I stepped away from the counter, away from Dragon and Defiant.  My foot had started to fall asleep where I'd been sitting on it, and I felt a touch unsteady anyways.



``You don't want to hear the answer to that question, either,'' Defiant spoke, behind me.



Dragon and Defiant had flown in, apparently to say hi, and so that Defiant could make something resembling an apology as part of his twelve step assholes anonymous process.  With the chaos the PRT had been facing as of late, and their own preoccupation with their mission, they hadn't been notified of the quarantine procedures.  They'd been questioned, they'd divulged that I was here, and the bigwigs giving the orders used Dinah to plot out a means of attack that would be likely to get me into custody.



Each idea seemed so much worse than the other, if I considered it for even a moment: either the PRT was using Dinah just like Coil had, or that Dinah had volunteered the information of her own free will.



I was willing to take Defiant at his word.  I didn't want to hear the answer.



``What are the odds?'' I asked.  ``Do you know?''



``I can ask,'' Dragon said.



``Please.''



She paused.  ``Ninety-six point eight percent chance we bring you into custody,'' Dragon said.  ``We have the numbers on general paths you might take to escape.  You understand if I don't give you the chance of success on those numbers, but you should know that violence won't work.  Less than one percent chance of success.''



``Ah.''  It was all I could bring myself to say.



\emph{It explains why they're playing it safe.  It's not just that I have a penchant for problem solving.  Dinah told them to watch out for it}.



I glanced at the crowd.  They were still listening.  Emma was there, hugging her arms to her body, eyes wide and uncomprehending.



Not even a factor.  On the list of things I had to deal with, she wasn't even in the top ten, not even in the top one-hundred.  I felt irrationally offended that she was here, as if she was only doing it out of some kind of self-importance.  As if she'd had a choice.



A part of me, bigger than I'd expected it to be, wanted to lash out.  To hurt her just because I \emph{could, }to answer that outrage I was experiencing, in regards to something she had no control over.



It wasn't like I had much to lose.



``Skitter,'' Dragon said.  She made it a warning, almost like she had with Defiant.  I couldn't be sure what she was warning me about.  Was my line of thinking that obvious?



``I never liked that name,'' I said.  ``Skitter.  Never quite fit.''



``If there's something else you'd like us to call you\ldots'' she trailed off, inviting an answer.  Her voice was gentle, as if she were talking to someone on a ledge.  I noticed Clockblocker was standing beside her, his glove pointed at me, fingers outstretched.



\emph{Was} I on a ledge, in a matter of speaking?  I could hardly tell.



``No idea,'' I said, as I walked around a table to put students between myself and Clockblocker. ``Felt like commenting on the subject.''



``You know how capable the precog is,'' Defiant said.  ``Come quietly, and we can all talk to the authorities together.  If it would help, I can admit some culpability in your current circumstance.  All of us together might be able to get you a more lenient sentence.''



I was aware of the eyes of the other students.  There was the cluster at the back of the room, the ones who were backing away from me, cringing, cowering.  Others hadn't left their seats, and were arrayed around me, their heads turning to watch me as I walked down the aisle.  The ones who'd stayed, less afraid, or more willing to face their fear.



He was admitting it, loud enough for everyone to hear.  He was partially to blame for me being\ldots this.  A crime lord.  A villain.  Partially.  Much of the fault was mine.



Strange, to be confronted with the realization \emph{here}, at school.  Not the place where it all started, but close enough.



``Okay,'' I said, more to myself than anyone else.



``Yes?'' he asked, taking a step forward.



``No,'' I told him.  He stopped in his tracks.  ``That was more of an okay, I've decided what I'm doing.''



I could see him tense.



``Students!'' I called out, raising my voice.



``She's taking hostages,'' Dragon said, her jetpack kicking to life.



``\ldotsa clear shot,'' Clockblocker said.  He was walking briskly to his left, his glove still trained on me.



``I'm \emph{not} taking you hostage,'' I said.  ``It's really your choice how this plays out.  I'm not sure if you heard me say it before, but I described you as a jury.  Now it's time for you to vote.''



``That's not how it works, Skitter!'' Defiant shouted.  He stepped forward, then whipped around to kill the swarm that was flowing in through the doorway behind him.  I could divert some to the air ducts, but it didn't amount to much.  He was stuck near the door, unless he wanted to let the bugs stream in.



``Stand if you side with me,'' I called out.  ``I won't make any big speeches here.  That's not who I am.  I won't feed you lies or guilt you into this.  It's your call.''



What had I expected?  A handful of people, Charlotte included?  A slow, gathering buildup?



Of the three hundred or so students in the auditorium, nearly a third stood from the benches where they'd sat.  As a mass, they migrated my way, gathering behind me.  Charlotte stood just to my left, staring forward without making eye contact with me.



Since I'd entered the school, I'd been acutely aware of the distinctions, the difference between \emph{then} and \emph{now}.  The sense of the Undersider's presence in the school had followed me, nagging at me.



What use were followers if we couldn't use them?



I heard movement, and glanced over my shoulder to see Charlotte's friend, Fern, breaking away from the mass of students at the very back of the room.  Nineteen out of twenty of them were the clean, pristine, bright-eyed kids who'd left the city when the trouble started.  As Fern advanced, eyes to the ground, others broke away from the crowd to join my group.  Not many.  Ten or twelve.  It was still something.



A hundred students and change, a small handful of bugs.  I could see Emma, standing on the sidelines, her fists clenched.  She was saying something, repeating it over and over, under her breath.  I couldn't spare the bugs to listen in.  I wasn't sure I cared.



``This is reckless,'' Defiant said.  His voice had a strange tone to it, and it wasn't just the digital \emph{twang }that I was hearing at the edges of the words.



``Probably,'' I replied, raising my voice enough that it could carry across the room.  ``But not as much as you'd think.  We're not fighting.  I stress, we're not engaging you.''



``What \emph{are} you doing, if you're not fighting us?'' Clockblocker asked.



``Defiant and Dragon wanted to use the hostages against me, putting me in a lose-lose situation where I was caught between \emph{them }and having to hurt people to try to escape.  I think I'm turning the tables, now.  We're going to walk out of this school as a group.  If you want to stop us, you're going to have to hurt us, and you aren't capable of doing that to people any more than I am.''



``Skitter!'' Dragon raised her voice.



``Taylor,'' I answered her.  ``I'm just Taylor, for just a little while longer.  I suppose I'll be retiring my civilian name, one way or another, by the end of the night.  Fuck you for that, by the way.  I won't forget it.''



``\ldots wasn't me,'' she said, and I doubted even Clockblocker heard her, from where he stood beside her.



``It wasn't your choice,'' I said, ``But as long as you choose to follow them, you're as culpable as they are.''



I hadn't even finished my sentence when I raised a hand and pointed.  There was a moment's hesitation, and then the group advanced.  I waited a few seconds, and then joined them, falling in step.



Clockblocker used his glove, and the fingertips shot out with explosive force, with what looked like gleaming white fishing line stretching between the digits and the glove.  The tips punched into a wall.  A fence of thin lines, not much different from my spider silk.



Dragon put her hand on the glove, and the tips retracted just as fast.  My bugs could hear her speaking.  ``\ldots'll hurt \ldots civilians.''



A few members of the group broke away before getting too close to the capes.  Others joined in.  The group marched forward, reaching the front of the room.



Someone pushed a piece of clothing into my hands.  A sweatshirt.  I pulled it on and flipped the hood up.  I took my glasses off, sliding them into a pocket.



Clockblocker was pressing through the group.  He'd used his power, but the press of bodies was actually causing some damage, as people unwittingly pushed others into the frozen individuals.  He was fighting to reach me.



``Link elbows,'' I said, my voice low, ``Surround him.  He's only about as strong as you are.''



It took a second for people to get organized.  He passed perilously close to me, but his eyes moved straight past me.  A few heartbeats later, the members of the group who had managed to get themselves linked together had him surrounded.



``Everyone to my right, head for the front door.  Everyone to my left, to the kitchen.  Straight past Defiant.''



The man barred the door.  We were only a dozen feet away when he slammed the butt of his spear into the ground.  Electricity and hot air ripped through the serving area of the cafeteria, with visible arcs dancing along the edges of sinks and the metal rails meant for the trays at the front.



``Steady forward,'' I said.  ``First ones to reach him, grab him.  You don't need to do anything except hold on.  Dogpile him, and he won't be able to move for fear of hurting you.''



I saw some people hesitating.  The group almost lost its forward momentum.



``He might not be a good guy,'' I murmured.  ``But he's a hero.  Trust in that.''



\emph{Or is it the other way around?}  That apology sat oddly with me.



He held his spear out horizontally, barring our path.  It was Charlotte that quickened her step, reaching out to fold her arms around the spear and his left hand.



Others soon did the same.  He stood tall in his armor, nearly seven feet, and people almost had to climb on top of him to find a place to hold on.



I almost wondered if I'd had a second trigger event, if I was controlling them, the image was so bizarre.



Then I took a better look at them, at how some weren't listening to me at all, retreating.  Others were being far less consistent, showing a wide variety of emotions.  Sheila, the girl with the side of her head shaved, was among them.  Her face was etched in \emph{anger}, of all things, as she clung to Defiant.



A hundred students had joined me, and a hundred students had their individual stories.  Their sleepless nights, their individual tragedies and moments of terror.  That was all this was.



I wasn't sure if that was a relief or if it was \emph{scarier}.



Dragon flew over us, her jetpack carrying her into the air, over the crowd.  Students were following beneath her, \emph{running}.  One or two leaped onto tables and jumped to try to catch ahold of Dragon's foot, but she veered easily to one side.



With Defiant occupied, I was free to bring bugs in through the back door, not having to worry about them being bug-zapped to oblivion.  I directed them straight into the vents on the jetpack that were sucking in huge quantities of air.  One second it was like a vacuum, drawing in air, the next it was clogged.  She lost lift, floating to the ground, and deftly batted aside the reaching hands of the students who were getting in her way.



Her jetpack expanded with an almost explosive motion, fanning out to have four times the number of intake vents, four times the number of output charges, and two laser turrets that curved over her shoulders.



There was no way she could pack that much machinery in that much space.  Either it was all crammed into her torso, which was impossible, or Armsmaster-Defiant had tweaked it.



She had liftoff, and she was \emph{faster}.



And I'd already slipped past Defiant, stepping into the kitchen, and into the narrow hallway.  She didn't have room to navigate, with the other students who were crammed into the entryway.



She turned herself around a hundred-and-eighty degrees and flew out the entrance of the cafeteria, heading outside.



Only twenty or so students were with me, now.  Dragon was stopping beside Adamant and Sere.  Adamant took her hand, and she lifted off, carrying the pair of them.



Still had to deal with three heroes\ldots



And the massive armored suits that the two had ridden in to arrive.  Two.



``No,'' Defiant said.



``You were supposed to \emph{protect} us!'' a girl shouted.  Sheila, the one who'd been angry, who'd brought a weapon to school and had left the school rather than relinquish it.



``I won't,'' he said.



He was talking to someone else.  The vents on his mask were open, hot air flowing out.  Was he trying to disperse heat so he wouldn't burn any students?



``It's still crude,'' he said, ``\ldots do more harm than good.''



There was a pause.



``\ldotsr freedom isn't worth possibly losing \emph{you}.''



Defiant, still at the serving area of the cafeteria, moved.  With nine students clinging to him, he was glacially slow, careful to a degree that I might have called agonizing, if it weren't so much to my benefit.



He needed two hands on his spear to remove the panel in the middle of the shaft.  I filled it with my bugs, and he shook it, to try to get them loose.  When that failed, he disconnected his glove, letting it strike a student that clung to his leg, before falling to the floor.



I tried to use my bugs to bite his hand, but I found it was a smooth texture, not flesh.  Metal or plastic, or something combining the two.  He found three buttons in the mechanisms inside the spear and typed in a sequence.



Dragon veered toward the ground, depositing the two capes there before staggering forward in four or five rapid footsteps, dispersing the rest of her forward momentum.  She fell into a crouching position.



We made our way outside.  The armored suit that Defiant had piloted to the school loomed before us, a four legged mechanical dragon perched on the athletics field, replete with panels of knightly armor.  This thing\ldots this wasn't a fight I could win.  Simple A.I. or no, Dragon would have shored up any weakness in logic.



It didn't move.



We walked between its legs on our way to the parking lot.  There wasn't really another route.



Dragon stood, abrupt, and I flinched.



She turned her head our way, but she didn't pursue, as we walked through the parking lot to the main road.  Adamant and Sere were too far away, Kid Win hadn't been willing to venture outside a second time, after the faceful of bugs I'd given him before.



Stray bugs drew out an arrow, pointing him to his things.  No use letting some stupid kid get their hands on it and blow their faces off or something.



I watched Dragon with my swarm, for as long as she was in my range.  I was well out of sight by the time she finally moved.  The students had released Defiant, and he approached her side.



She extended a hand, and it tremored, the movement stuttering, palsied.



Defiant seized it in his right hand and pulled her close, wrapping his gloveless arm around her shoulders.  He set his chin on top of her head.



My escort and I walked as a group until we were three blocks away from the school.



``Stop,'' I said.



They did.  The remaining members of the group backed away, turning towards me.



What was I even supposed to say?  `Thank you' seemed so trite.  They were all so different.  There was Fern, and a boy who didn't look like one of the ones who'd stayed in the city.  Some looked nervous, others showed no expression at all.  There was no response that encapsulated all of them.



I tried to think of something to say, but the harder I tried, the less anything seemed to fit.



``You saved my dad,'' Fern said, as if answering a question I hadn't asked.



\emph{Saved her dad?}  When?



It didn't really matter.



``Imp found the bastard who was threatening to do shit to my little sisters,'' one guy said. ``Tied him to a traffic post.  And you work with her, right?''



``You fought the Slaughterhouse Nine.''



``\ldotsthose bastard ABB guys\ldots''



``Fed\ldots''



``\ldotswhen Shatterbird\ldots''



``\ldotsMannequin\ldots''



``\ldotsLeviathan showed up at the shelter, I heard you were\ldots''



``\ldotsEmpire\ldots''



A collection of voices, a jumble, to the point that I couldn't take it all in.



\blacksquare



I didn't have a group with me as I walked down Lord street.  I turned right, onto familiar territory, my heart heavy.



It wasn't long before I was close enough.  My range was longer, now.  Odd.  It was supposed to get longer when I felt more trapped, but `trapped' wasn't the word I would have chosen.



My bugs rose at my command, tracing over the area.  It wasn't so unusual, that there were flies, bumblebees and ants about: the heat of summer, the humidity, the imbalanced ecosystem\ldots  Nobody paid them any heed.



A small butterfly found its way into the house.  It traced over the glossy smooth armor and helmets of PRT officers, touched the badge on the chest of a police officer.



It touched my dad's shoulder, moved down his bare arm to his hand.  He was sitting at the kitchen table, his head in his hands.



An officer swatted at the bug, missing.  The action drew someone else's attention.



``It could be her,'' the woman in the PRT uniform said.



``Fan out!'' someone else ordered.



They spilled out of the house.  Orders were shouted, and people climbed into cars, peeling out.



Still at the kitchen table, my dad reached out for the butterfly.  I had it settle on his finger.  Cliche?  Overdramatic?  Probably.  But I couldn't bear for my possible last contact with my dad to be through anything ugly.



``Taylor,'' he said.



Six and a half city blocks away, I replied, ``I'm sorry.''



The butterfly and I took off at the same time.





