





``Park there,'' Stan said, pointing to a space off the side of the road.



``We'll be facing uphill, and we still have to unload the equipment,'' Nipper piped up, from the back seat.



``There's a method to my madness.  Park, Marshall.  I'll even deign to help unload and carry this time.''



He got a glimpse of Marshall rolling his eyes, but the boy steered the van to a parking spot.



True to his word, Stan was out the door, rolling up his sleeves.  Didn't hurt: the humidity was brutal outside the air-conditioned van.  His dress shirt was already sticking to his back.



They were on a hill, and the vantage point afforded them a view of the city.  Cranes dotted the skyline, and the buildings themselves were gleaming, the whites and colors brightened by the ambient moisture in the air.  It might have looked attractive, but there were spots where buildings were missing, whole areas where the construction was only just beginning.



He could see the white building, not too far away, which was taller than even the skyscrapers immediately around it.  He'd investigated it just a few days ago.  They'd erected a tall white tent, holding it up with a crane, they'd reinforced it with plexiglass panels and iron reinforcement, and now a more solid construction was going up around it.  Slow, painstaking, careful work, filled with redundancies.  The workers would be glad to be free of the hazmat suits in this heat.



Brockton Bay wasn't lacking in stories to tell.  The quarantine building alone was one.



``Need a hand,'' Nipper said.



He hurried around to the back of the truck.  The van had been parked at the side of the road, emergency brake cranked, wheels turned so it would ride up onto the sidewalk if the brake failed, but the steep incline was making it hard to unload the equipment.  Much of it was set up to be slid out of the back of the van at a moment's notice, but that same convenience was an obstacle, here.  The stuff was expensive, and if it slid to the road\ldots



He found a space beside her and reached to get a grip on the far end of the camera.  It might not have been a problem, but Nipper was short, petite, built more like a thirteen year old than a twenty-three year old college graduate.



She wasn't suited for the job.  She knew the equipment, she was capable with a computer, she had good eyesight, and the tattoos and array of piercings on her right ear were as good an indicator of her creative edge as anything else.



But this wasn't the job she'd been working towards.  She wasn't one to complain, but she didn't have stamina, she didn't have strength, and this, all of this, it was too fast paced for her.  She'd have been better, maybe even \emph{happier} in the newsroom, managing the feeds, maintaining the systems and working on post production.



Marshall hefted the bag out of the back of the van.  All the wires, the tripod, the lighting, packed into a dense case.  The boy didn't look like a professional, hadn't quite adapted to the job he'd been pulled into: from intern to a jack of all trades, filling in the gaps in Stan's team.  Set up, interviewing, driving, gopher\ldots anything and everything.  He was drawing in a paycheck, but he was definitely working for it, facing all of the hassles, the intense stresses and dangers of the job, for eleven dollars an hour.



\emph{Dangers}, Stan thought.  Images flickered through his mind.  Everyone at the station had seen the feeds, had watched them several times over.  Purity taking the camera from Manzaneres, a guy from channel four, then setting her monsters on the man.  A man with a wife and a newborn had been murdered, just to make a point.



There was a reason for the shortage of field reporters.  It wasn't limited to Manzaneres, either.  The problem was a chronic one.  This was a job that put ordinary people on the fringes of events that were dangerous for \emph{capes.}



``Set?''



Marshall closed the back of the van and locked it.  ``Set.''



Stan set off, with Nipper and Marshall following, Nipper almost jogging to keep up with his long strides.  ``Reason we're parked here is that the school's on top of the hill.  We don't know how much parking there'll be, with students possibly taking up spaces, and if we have to drive by, searching for a spot, then someone's liable to spot us and take measures.''



``Measures?'' Nipper asked, a touch breathlessly.



Right.  She didn't have the experience to know.  ``You'll see what I mean.''



There were students gathered outside the walls that bordered the school.  Police cars were parked at the front, along with PRT vans, but it was the uniformed guards with `Arcadia High School' stenciled on their sleeves that caught his attention.



\emph{Guards?  }It conjured up an image of a prison, rather than a school.



``Nip, get some footage of the uniforms,'' Stan said.



She hefted the camera and trained it on the nearest of the uniformed guards.  She had to slow her pace to keep the shot steady, but she kept following him.  When a group of students obstructed her vision, she shut off the feed and hurried to catch up.



They reached the gate, where a woman with a colorful scarf was talking to a PRT uniform.  He signaled Nipper, and the young woman raised the camera.



``Damn it,'' the woman with the scarf groaned, as she saw them.  The police officer took the opportunity to step away.



``Don't jump to conclusions,'' Stan said, ``We're not the enemy.''



``You're here to bog down an overcomplicated situation,'' she said.  ``I have enough problems without vultures descending.''



``We're here for the story, that's all.  You're in charge here?''



``I'm in charge of the \emph{school.  }Principal Howell.''



He made a mental note.  \emph{Howell, Howell, Howell.  }She wasn't the prettiest woman, with old acne scars riddled across her cheeks, a short stature and a nose that didn't quite fit her face.



``Stan Vickery, channel twelve news,'' he flashed her his best smile and extended a hand.  She didn't take it.



``You're not allowed on school property.''



``I would be if you gave me permission,'' he said, dropping his hand.  The job was politics as much as it was investigation, creativity and presentation.  What did she want?  Peace and quiet.  ``Give us fifteen minutes to talk to your students and shoot a few takes in front of the doors, and I'll get the word out that we got the story first.  Other stations are playing it safer, these days, less crew, less willing to act on sloppy seconds.''



The principal made a face.



Stan smiled, ``Sorry.  You get what I mean.  Give us fifteen minutes, and we're one \emph{less} thing you have to worry about today.  With luck, I'll be the only local reporter you see today.''



``With all due respect, Mr\ldots''



``Vickery,'' he said, \emph{already told you my name.}  ``But you can call me Stan, Mrs. Howell.  Fact of the matter is, you let me in the school, and I \emph{owe} you one.  I pull strings or emphasize certain aspects of a story.  Not just this one either.  Who knows?  The next incident could be worse, or more sensitive.''



``Mr. Vickers,'' she said.  ``I'm fully aware that you're trying to bait me into giving you a sound bite.  I won't comment on this situation, and I won't be letting you onto school grounds.  I don't want you talking to any\emph{ }of my students.''



``Fine,'' he said.  ``Come on, guys.  Let's go talk to the cops.''



``Seriously?  We're giving up?'' Nipper asked.



``Yes,'' he said, he took long strides away from the front gate of the school, until he was sure the principal wasn't in immediate earshot.  ``No.  She's liable to get on our case if we don't pretend to play along.  Howell has no authority outside of the school walls, so we interview students there.  Marshall, head back in the direction of the van.  Talk to students, see if they want to be on TV.  Look for the talkative ones and the emotional ones, and point them my way.''



``What about the cops?'' Marshall asked.



``They'll be around later, and cops have better memories than civilians.  It's the students who were at the scene.  Go.  We don't know how long we have before other crews show.''



It was a shame the principal hadn't let him into the school, Stan mused.  Silly of her, too.  That favor he'd offered her was gold, all things considered.  Something she could use to bail a superior out of an awkward position and advance her own.



\emph{Your guanxi could be better}, \emph{Mrs. Howell}, he thought.  He loved the idea behind the Chinese concept of guanxi.  It fit in the same general category as the concepts of friends, family, acquaintances, but it was more based in business and politics.  Guanxi was about being able to call up a person one hadn't seen in years and ask for a favor.  To have enough people in one's debt that there was more implied leverage to use when seeking favors from others.



He'd been introduced to the idea a few years ago, and he attributed much of his recent career advancement to it.  It was something to be aware of at all times, and it changed his perspective on things.



He approached a group of teenage girls who were gathered in a group, observing the police and PRT officers.  He flashed one of his best smiles at them.  He could see one of them glance him over, her body language changing subtly.  He directed the smile at her, ``I bet you're \emph{dying} to talk about what happened here.  Exciting stuff.''



``Sure,'' the girl replied.  ``Supervillain doesn't attack the school every day.''



``Wasn't an \emph{attack}.  She showed up, and they came after her in her civilian ID.''



``I know it wasn't an \emph{attack},'' the first girl replied.  ``I was just\ldots It's what others have been saying.''



``Skitter, wasn't it?''  Stan chimed in.  He snapped his fingers, and Nipper pointed the camera at the girls.



``Yeah.  The bug girl,'' another girl spoke up.  ``I guess she goes to Arcadia.''



``No way.  I heard she was a student at Winslow, before Leviathan came.  Geeky kid, was having a hard time with some jerks, apparently.  I think her name was Taylor, but you'd have to ask someone from Winslow.''



He prodded, ``What happened?  Was there a fight?''



``Dragon and this new guy Defiant showed up, along with the two new heroes.  Don't know their names.''



He'd memorized the names.  ``Adamant?  Clasp?  Dovetail?  Halo?  Crucible? Rosary? Sere?''



``Sere and Adamant,'' one girl replied.



``Sere and Adamant,'' he said, making a mental note.



``And two of the Wards.  Clockblocker was one of them.  Anyways, she got away.''



``She didn't do anything to provoke them?''



``Didn't hear about anything.''



``And they mobilized on the school?''



``Sure.''



He started to ask for more details, then stopped.  Marshall was approaching, with a kid in tow.



``Cell phone video,'' Marshall said.  ``Long conversation between Defiant, Dragon and Skitter in the cafeteria.



Stan raised his eyebrows, looking at the girl with the phone, ``Pay you twenty bucks to let us copy it.''



``A hundred,'' she said.



``Twenty.  If you got it on camera, others did too, and \emph{someone}\emph{`s} going to take the twenty.''



She glanced at Marshall, then back to Stan.  ``Fine.''



``You have the equipment?'' Stan asked Marshall.



``Laptop and a cord.  Give me a minute.''



``We'll watch it later,'' Stan said, absently.  He turned his attention back to the girls.



This wasn't the first time he'd walked into a situation almost blind.  The job was a stressful one, but he thrived on stress.  Racing against the clock, to be the first to the scene, the first to report on the situation.  But even reporting was a kind of challenge unto itself.  The scene had to be investigated, the story teased out, details verified.  To top it off, it had to be \emph{presentable}.



He'd been the producer, before Coil had blown up the camera crew and reporter that had been covering the mayoral debate.  He had an eye for this.  Had to, because there was nobody back at the studio that would be able to cover this base for him.  Sad and ironic, really.  There weren't enough people in the bay, resources weren't consistent.  So they'd reduced the size of the staff, cut back on hours.  Then six people had died, including their lead reporter.



Nevermind the rumors that the PRT was, on Miss Militia's behalf, investigating ties between Coil and the killed reporters and camera crews.  He'd \emph{itched} to look into that more, but it didn't fit with his philosophy.



``Were you there, in the cafeteria?'' he asked the girls.



``No.''



``Right.  Alright.  Any thoughts?  Were you scared, knowing there were so many capes in the school?''



Twenty more seconds, to grab more details and reaction clips, and then he was moving, searching for others to talk to.



Two more groups questioned, and he didn't have much else.  He knew Skitter's name, and Channel four had arrived, and the race was on.



``Got the video!'' Marshall called out.



Stan took the offered laptop.  To watch now, it would mean delaying interviews.  Memories would fade.



But he needed the narrative.  How had things unfolded?  What were the key, crucial points at the heart of this?  That the school was unsafe?  It would work, grab attention and viewers, but it felt cheap.  No, the public knew that the Protectorate was imploding.  There had to be a connection, tying this to something greater.



``Thank you,'' he said.  He'd decided.  ``Now, I need you to find me someone who knew Skitter in her civilian guise.''



Marshall nodded.



``He or she will be one of the students who attended Winslow.''



``On it.''



Stan retreated to the van with the laptop.  He took the extra time to open the video in an editing suite before playing it.



Without being asked, Nipper hooked it into the van's computers.  A little icon notified him that he was connected to the studio.



``\emph{\ldotsThere for the S-class threat downtown.  I don't want to sound arrogant, but I think maybe I deserve to, a little.  I've done my share.  You don't turn around and reveal my identity in front of a crowd}.''



On a notepad of lined paper, he penned down '20th' followed by a question mark.  The video continued playing, and he noted down times and key phrases, along with questions.  When a critical comment was shown, he was sure to copy the clip.  There were a few times where the volume was too quiet, the voices too low or things were drowned out by background noise.  Nipper worked to tune the sound so they could make it out, raising the volume or filtering out the noise.



D&D picked fight?  Pushed by authorities?Drag past convo with Skitter.  When?
Putting children at risk
Violation of truce



``\ldots\emph{And you seriously expect me to keep my mouth shut about all the dirty little secrets I've picked up on over the last few months}\ldots''



\underline{What does Skitter know}?  App'tly important.



``\ldots\emph{the Slaughterhouse Nine.  Either you've abandoned that chase, or you're about to tell me that there's something more important than stopping them}\ldots''



S9?  D-check events post-Boston.



Hospital?  Skitter & Defiant?



D&D negotiating with villains?  Possible cooperation?  Corruption?



``\ldots\emph{Stand if you side with me!}''



Both video and audio were distorted by the movements of students, rising from tables, pushing away from the jumble of bodies.



Stan smiled.  \emph{There}.



He cut out the scene in question, the students siding with Skitter over the heroes, and gave the clip a title.  `The heart of this story?'



A second later, a note appeared on the side of the window.  The crew at the studio had a R.A.T. connecting them to the laptop, and freedom to make changes or add their own details.



Yes – Ed



He had it.  The editors at the station were on board.



Now to cobble it together into a \emph{story}.



He opened a file and began sketching out the script.  At the very top, he put up notes, clips he'd need from the station.



There was a knock on the door of the van.  Stan opened it to see Marshall with an awkward looking young man.  Fifteen or sixteen.  He looked despondent.  Hangdog.



``He says he was her friend, once.''



``No,'' the boy said.  ``Not exactly.  But we sort of knew each other.  Had classes together, did group work.  And I owe her.''



Stan smiled.



\sectionbreak



``\emph{\ldotstake you now to reporter Stan Vickery.''}



``\emph{Thank you, Nick.  One thousand and two hundred students made their way to Arcadia High for their first day back at school, earlier on this sunny day.  They hoped to readjust and get a taste of normal life after weeks spent away from home, or enduring the long series of incidents to afflict Brockton Bay.  Less than halfway through their day, those hopes were dashed.}``



A video clip replaced the blond man with the mustache and a face lined by years of stress.  A massive metal suit, looming at the far end of the school's parking lot, a mechanized dragon.



``\emph{The school became the site of a confrontation between Dragon, a heroine known across the world, and local warlord and leader of the Undersiders, Skitter.  Within moments of their meeting on school grounds, Dragon revealed Skitter's identity as Taylor Hebert, a sixteen year old student.  With this revelation came a dozen more questions\ldots}``



``Change the channel,'' a boy in prison sweats said.  ``News is boring shit.''



``No,'' Sophia said.



\emph{Skitter was Taylor}.  A dozen things fell into place.



Anger boiled within her.  Outrage.  That cringing, whiny, pathetic little scarecrow was the ruler of Brockton Bay's underworld?  It didn't fit.  It \emph{demanded} an answer of some sort.



But she couldn't.  As the voice droned on, Sophia turned her attention to the bracelets she wore.  There was a live current running through them, and they could be joined together to fashion handcuffs, but even like this, they were bondage.  She couldn't enter her shadow state without passing through the insulated sheath that protected her.



She couldn't leave, as much as she wanted to, right this moment.



Glowering, a confused, \emph{impotent} frustration building within her, she fixed her eyes on the television.  It swelled within her until she could barely think.  She clenched her hands, but she couldn't squeeze hard enough to release any of the building emotion.  She unclenched her fists, extended her fingers, as if reaching for something, but there was nothing she could grab.



There was no release valve for this, no way to vent.



Taylor's face appeared on the screen in the same moment she hit her limit.  She rose from her seat, aware of the guards advancing on her, and kicked the television screen, shattering it, amid the protests and swearing of her fellow inmates.



A second later, they were tackling her.  Two guards at once, forcing her to the ground.



She screamed something so incoherent that even \emph{she} would have been hard pressed to interpret it.



\sectionbreak



``\emph{Who was she?  And what motivated these professed heroes to mobilize on a school, risking the lives of students and staff?  Skitter herself wondered aloud about their willingness to put hostages within her reach\ldots}``



A clip appeared on the screen.  Taylor, sitting on the edge of a counter.  She spoke, filled with confidence, almost nonchalant.  ``\emph{You put me in a room with three hundred people I could theoretically take hostage.  Why?  You can't be that confident I wouldn't hurt someone\ldots}''



A student abruptly shrieked, thrashing and falling to the ground in her haste to get away.



``Danny,'' Kurt said, settling a hand on his friend's shoulder.  ``You don't need to watch this.''



Danny shook his head.  Kurt looked down the man.  He hadn't even spoken, from the moment he'd opened the door and Lacey had wrapped her arms around him.



``\emph{This is bait, isn't it}?'' Taylor's voice, oddly out of place coming from the television.



``\emph{The tone of the conversation even implied there were unspoken secrets that Skitter was aware of, that the Protectorate sought to silence,}'' Stan Vickery spoke, reappearing, with Arcadia High behind him as a backdrop.  ``\emph{Raising questions about what those secrets might be.}``



``\emph{\ldotsYou seriously expect me to keep my mouth shut about all the dirty little secrets I've picked up on over the last few months?}''  Taylor's voice, again.



Danny put his face into his hands, pushing his glasses up to his forehead in the process.  Kurt rubbed his back, while Lacey looked on, sympathetic.



``\emph{What did Skitter know, and does it relate to the event  on the twentieth of June?  Why were Defiant and Dragon willing to abandon their pursuit of the Slaughterhouse Nine?}``



``Is\ldots'' Danny started to speak, but his voice cracked.  He paused, then spoke again.  ``Is this on me?''



``No!'' Lacey said.  ``No, honey.''



\emph{``Those aren't questions I'd hope to pose any answers to today},'' the news reporter said.  ``\emph{The real question is bigger than that, and smaller at the same time.  What forces drive a child from this\ldots}``



A teenage boy, his eyes downcast.  ``\emph{She was nice, quiet.  I know people won't believe me when I say it, but she was a genuinely good person.  Is.  Is a good person.  At heart.  I'm sorry, Taylor.}``



``\emph{To this?}``



It switched to Taylor's voice, calm, unruffled, accompanied by the same long-distance, low resolution footage of her sitting on the counter in the school cafeteria.  ``\emph{You'd be surprised what I'm capable of.  I've mutilated people.  Carved out a man's eyes, emasculated him.  I've chopped off a woman's toes.  Flayed people alive with the bites of thousands of insects.  Hell, what I did to Triumph\ldots he nearly died, choking on insects, the venom of-}``



Kurt turned off the television.  Danny was frozen, unmoving, staring down at his hands.



``It was context,'' Lacey said, quiet.  ``She was acting.  I'm sure-``



She broke off as Kurt shook his head.  \emph{Doing more damage than good}.



``We're going to stick by you, okay, Dan?'' Kurt spoke.  ``Let's have you come by our place.  Better you aren't alone right now, yeah?  And it'll get you away from those reporters.''



Danny didn't respond.  He stayed hunched over the kitchen table.



``Unless you want to wait here for her, in case?'' Lacey asked.



``She already said goodbye,'' Danny replied, pushing against the table to help himself rise to a standing position.  ``I think that's it.''



\sectionbreak



``\emph{You'd be surprised what I'm capable of.  I've mutilated people.  Carved out a man's eyes, emasculated him.  I've chopped off a woman's toes.  Flayed people alive with the bites of thousands of insects.  Hell, what I did to Triumph\ldots he nearly died, choking on insects, the venom of a hundred bee stings making his throat close up.}``



``\emph{And what drives dozens of students to reject the heroes of this city in favor of the villain in charge?}''  Stan asked.



The widescreen television showed the students rising from the tables, joining Skitter.  Another clip followed, showing students actively wrestling with the heroes.



``Christ,'' the Director spoke.



Beside her successor, Piggot was watching in silence, elbows on the table, hands folded in front of her mouth.



``This could have been avoided,'' the Director said.  ``On multiple levels.''



``Most likely,'' Defiant replied.  He stood at one end of the long table, Dragon beside him.



``If you would have cut off the feed, deleted the footage from phones, we would have had time to do damage control.''



``We won't ignore people's first amendment rights,'' Defiant said.



``\emph{\ldotsThe PRT and the Protectorate have refused to comment, and the silence is damning, in light of what occurred today,'' the reporting continued in the background.  ``Brockton Bay has become the latest, greatest representation of the troubles the world faces in this new age, and perhaps a representation of the world's hopes\ldots}``



``You're better than this, Dragon,'' Piggot spoke.  ``To the point that I'm left wondering\ldots did you steer all of this in this direction?''



``If you try to place the blame on us,'' Defiant replied, ``I think you'll be unpleasantly surprised.''



``\emph{This event},'' the reporter spoke, ``\emph{Points to something else entirely, a fatal flaw in the system, the latest and greatest representation of the Protectorate's steady collapse.}``



Director Tagg, Piggot's latest successor, picked up the remote and muted the television.



Defiant shifted his weight, clasping his hands behind his back.  The body language was \emph{smug}, somehow.



Piggot glanced at each of the people who were seated at the table.  Mr. Tagg, the Director of Brockton Bay's PRT, Director Armstrong from Boston, and Director Wilkins from New York were all present.  Mr. Keene sat opposite her.  A camera mounted on the table gave the Chief Director of the PRT eyes on the meeting, where she watched from Washington.



Nobody else seemed willing to answer Defiant, some simply staring at him, others watching the segment on the wall-mounted television.  She spoke, ``I would remind you that you are on a strict probation, with terms you agreed to.''



``I am,'' Defiant said.  ``Would you arrest me for being insubordinate?  Or would it take something more substantial?''



``Test us and you'll find out,'' Director Tagg responded.



``And what would happen then?  Would you send me to the Birdcage?'' Defiant asked.



The question was heavy with the reminder that it was \emph{Dragon} who maintained and managed the Birdcage.



Emily Piggot was caught between a desire to feel smug and quiet fear.  She'd warned them.  She'd communicated her concerns at every opportunity, through channels that Dragon wouldn't be able to track.  She'd been dismissed, shrugged off, when she raised the question of what might happen if Dragon was killed in battle, or if Dragon turned against them.



``I'd like to hear a response from Dragon,'' Piggot said.



Dragon turned her head to look at her, face hidden behind an expressionless mask and unblinking, opaque lenses.  There was something about the movement that seemed \emph{off}.  Both the movement and the silence that followed was oddly disturbing.



``No?  No response?''



``A consequence of our recent visit to Brockton Bay,'' Defiant said.  ``I'm hoping she'll be better in a few days.''



\emph{Curious}, Piggot observed, the note of emotion in his voice, at that simple statement.



As if eager to change the subject, Director Armstrong said, ``Mr. Keene.  Thoughts?  How does this affect your department?''



Piggot turned her attention to the man.  She'd only had limited interactions with him, but the man had earned her respect quickly enough.  He wasn't a Director, but rather the liaison between the Protectorate and various other superhero teams worldwide, organizing deals, ensuring that everyone held to the same code of conduct, and ensuring that the groups could all coordinate in times of emergency.



``It's catastrophic,'' Keene said.  ``I can manage some damage control, offer further aid, manipulate the grants available, but I can't build on a foundation that isn't there.''



``Where do our biggest problems lie?''



``The C.U.I. is first to mind.  The Suits and the King's Men will cooperate, because they have to.  For the American teams, it varies from case to case.  But we're in the middle of negotiations with the C.U.I., and this won't reflect well on us.  That is, it won't if we can't get our footing here and make a strong showing at the next major event.''



The next major event.  The idea seemed to give everyone pause.



``Something needs to change,'' Defiant said.



``Somehow, Colin,'' Piggot replied, ``I think our ideas on what needs to change are very different.''



``Very likely,'' he said, his voice hard.  ``But this was a last straw for us, in many ways.  We have a few stipulations for our continued assistance.''



``Defiant,'' Tagg interrupted him.  ``You're not in a position to make demands.''



\emph{He's a hard man,} Piggot thought.  \emph{Army, PRT squad leader, a general, not a politician.  Ironic, that they'd butt heads}.  ``Director Tagg, you asked me here as a consultant, so allow me to consult.''



Tagg turned his attention to her.



She continued, ``I don't like this scenario any more than you do.  But let's hear Defiant's demands before you reject him out of hand.''



Director Tagg didn't reply, but he turned his attention back to Defiant and he didn't speak.



``Dragon and I have discussed this in-depth.  We need the present Directors to admit culpability for the incident, and we need to clean house, with in-depth background checks and investigations into any prominent member of the PRT.  We can't maintain things as they are with the spectre of Cauldron looming over us.''



``You'd have us fire any number of PRT employees at a time when we're struggling to retain members?''  Tagg asked, almost aghast.



``And relieving capes from duty at the same time,'' Defiant said.  ``With so few employees, it's ridiculous to continue working to shut down leaks and control the flow of information.  Dragon has expressed concerns over having to do this in the past, and between the two of us, we've agreed that the censorship stops tonight, at midnight.''



Tagg rose from his seat, opening his mouth to speak-



``I agree,'' Piggot spoke before her successor could.



Heads turned.



``It's a misuse of resources,'' she said, ``And we do need to clean house.''



``You don't have a position to lose,'' Tagg replied.



``I wouldn't lose it anyways,'' she retorted, ``I've had no contact with Cauldron.''



Keene clapped his hands together once, then smiled, ``Well said.  We have nothing to fear if we aren't connected to them.''



``You realize what they're doing, don't you?'' Tagg asked.  ``How does this investigation happen?  Dragon has her A.I. rifle through all known records and databases.  We defeat the sole purpose of the PRT, by putting the parahumans themselves in a position of power!''



``That ship has long sailed,'' Keene commented, ``With the revelations about Chief Director Costa-Brown, if you'll pardon my saying.''



``You're pardoned,'' the Chief Director's voice sounded over the speaker, crystal clear.  ``I think this would pose more problems than it solves.  We'll have to turn you down, Defiant.''



``Then I don't see much of a reason for us to stay,'' Defiant replied.



``And if you leave, the assumption is that we'll be left without Dragon's ability to maintain every system and device she's created for us.  The PRT without a Birdcage, without our computer systems or database, without the specialized grenade loadouts or the containment foam dispensers.''



``An unfortunate consequence,'' Defiant said.



``Not a concern at all,'' the Chief Director replied.



There was a pause.  Dragon glanced at Defiant.



``No?'' Defiant asked.



``No.  We've been in contact with an individual who has a proven track record with Dragon's technology.  He feels equipped, \emph{eager}, almost, to step into Dragon's shoes should she take a leave of absence.''



``Saint,'' Defiant said.  ``You're talking about the leader of the \emph{Dragonslayers}.  Criminal mercenaries.''



``My first priority is and always has been protecting people.  If it's a question between abandoning the security the Birdcage offers the world at large or requesting the assistance of a scoundrel--''



``A known murderer,'' Defiant said.



``I wouldn't throw stones,'' Tagg replied, his voice a growl.



``--A known murderer, even,'' the Chief Director continued, as if she hadn't been interrupted.  ``I will take \emph{security} without question.''



Defiant looked at Dragon.



``The second dilemma I have to pose to you two,'' the Chief Director continued, ``Is simple.  What do you expect will happen when the next Endbringer arrives?  Between Dragon's brilliant mind and Defiant's analysis technologies, I'm sure you've given the matter some consideration.  Without the Protectorate, how does the event tend to unfold?''



Piggot studied the pair, trying to read their reactions.  They were so hard to gauge, even if she ignored the armor.



``It doesn't go well,'' Defiant said.  ``It doesn't go well even if we assume the present Protectorate is coordinated and in peak fighting condition.''



``We can't afford a loss,'' the Chief Director said.  ``You know it as well as I do.  Now, tell me there isn't room for a middle ground.''



Dragon turned to Defiant, and moved with a careful slowness as she set one hand on his arm.



``We get through the next fight,'' Defiant said.  ``Then we clean house.''



``I think that's an acceptable compromise.''



\sectionbreak



``\emph{This event},'' the reporter spoke, ``\emph{Points to something else entirely, a fatal flaw in the system, the latest and greatest representation of the Protectorate's steady collapse.}``



``Too rich,'' Jack commented, smirking.  ``Across the board, I love it.  Fantastic.''



Hookwolf, pacing on the opposite side of the television, grunted a response.



Bonesaw was crouched by the side of a machine.  She watched with hands on hips as Blasto ratcheted in a bolt at the base of a tall, black-handled lever, his movements jerky with the internal and external mechanisms that forced them.



``\emph{The Protectorate declined to comment, and in light of recent events and allegations of deep-seated secrets, their silence is damning.}``



``Almost ready,'' Bonesaw said, her voice sing-song.  ``You're next, Hooksie.''



Hookwolf glanced at her, and then at the contraption.



``Don't tell me you're \emph{scared,}'' she said, her tone a taunt.



``Not of\ldots \emph{this}.  I'm questioning if this is the path we should take.''



``I'm expected to bring about the end of the world,'' Jack said, still watching the television.  ``But this is rather tepid for my tastes.  I'd like to hurry it along, inject some more drama into the affair.''



``\ldots\emph{event at Arcadia High School is sure to draw attention from aross America.  We, the public, want answers.  The death of Vikare marked the end of the golden age, the end of an era where becoming a superhero was the expectation for anyone and everyone with powers, and even those who decided to work in business or public affairs with their abilities were termed `rogues'\ldots}``



Bonesaw took ahold of Hookwolf's hand and led him to his seat.  She stepped back, glancing over the contraption.  The only light was cast by a small desk lamp and the glow of a computer monitor, an island of light in the middle of an expansive, wide-reaching darkness.  Desk, engine, and tinker-designed seats, surrounded by an absolute, oppressive darkness.



``It doesn't sit well,'' Hookwolf said.  ``I can't articulate why.  My thoughts are still cloudy.''



Bonesaw hit a button, and the lights began to flicker, the engine beside her starting to hum with a progressively higher pitch.  With the flickering of the lights came glimpses of the things beyond.  Light on glass and wires.



``I'd rather a Ragnar\"{o}k than-``



Bonesaw hauled on a white-handled lever, and Hookwolf's voice cut off.  The flickering of the lights ceased, and the room returned to darkness.



Jack sighed.



``\emph{\ldotsthreatens to mark a similar occasion\ldots}``



Bonesaw stepped over the body of a dead tinker in a lab coat, stopping in front of Jack.  ``Strip.''



Jack shucked off his shirt, and then pulled off his pants and boxer briefs.  The blades that hung heavy on his belt made an ugly metal sound as they dropped to the tiled floor.



``\ldotsand cover yourself up,'' Bonesaw said, averting her eyes.  ``Shameful!  You're in the company of a child, and a \emph{girl}, no less.''



``Terribly sorry,'' Jack said, his voice thick with irony, as he cupped his nether regions in both hands.  He stepped back and took a seat, leaning back against the diagonal surface behind the short bench.  \emph{Cold}.



``.\emph{..The reality is clear.  The repercussions of what happened today will change the relationship between hero, villain and civilian.  It remains up to them to decide whether it will be a change for the better, or a change for the worse}.''



The segment ended, and the television turned back to the news anchors at their desks.



``Pretentious, isn't he?'' Jack asked.



``Likes to hear himself talk,'' Bonesaw replied.  ``Which do you think it'll be?  Change for the better or change for the worse?''



Jack smiled.



``It's a given?'' she asked.  She pressed the button, and the lights started to flicker again.



``I think so,'' Jack commented.  ``But I almost hope things \emph{do} turn out well.''



The lights were flickering more violently now, to the point that periods of light matched the periods of darkness.  Between the spots in his vision, Jack could see more and more of their surroundings.



Row upon row of glass case lined the underground chamber, each large enough to house a full-grown man, though there were only fetal shapes within at present.  Each was labeled.  One row had cases marked `Crawler', `Crawler', `Crawler'\ldots ten iterations in total.  The next row had ten cases labeled with the word `Siberian'.  The one after with ten repetitions of `Chuckles'.



One column of cases dedicated to each member of the Nine, past and present, with the exception of Jack and one other.



``Makes for a greater fall?'' Bonesaw asked.



``Exactly,'' Jack replied.  He glanced at the one isolated case, felt his pulse quicken a notch.  It was the only one that was standalone.  `Gray Boy.'



``I guess we find out soon!'' he said, raising his voice to be heard over the whine of the engine.



Bonesaw only laughed.  She hauled on the switch with both hands, and the room was plunged into silence and darkness.





