





If Accord didn't know better, he might have thought this little soiree was located here with the sole purpose of irritating him.



Wait, he \emph{did} know better.  Tattletale.  She would have done this just to beleaguer him.



The Forsberg Gallery.  The building had once been a pristine, albeit distressingly asymmetrical construction of glass and steel.  Now it was a shattered ruin.  There was little rhyme or reason to the design, and navigating was something of a chore.



To his right, as he ascended a staircase, there was a wing that jutted out from the side of the building, six stories up, like an architectural tumor.  With the damage done by Shatterbird's attack, the only glass that remained in the building was scattered across the floor like a winter frost.  The offending growth on the side of the building had sustained some damage, more likely a consequence of the vibrations than damage from the glass itself, and the reinforcements that had been made to shore it up only served to make it uglier.



Inelegant, unbalanced.



His power immediately began supplying answers and solutions.  He was on his guard, and the first thoughts to his mind were of offense and harming others.  As clear as if he were seeing it for himself, he could see a pendulum, disguised among the steel frame of the building, swinging from a point above, and he could hear the sound of steel on steel, like a sword being drawn from its sheath, only at twelve times the scale.



With the appropriate design, the impact would be clean, almost muted.  His enemies, isolated within the wing, would make more noise, screaming as the reinforcing struts and the rivets holding intact beams to the larger structure were shorn away.  The end result would see his enemies dead, and the building improved, more \emph{balanced}.



Ten minutes to draw up the blueprint.  Eighty to a hundred minutes of labor, depending on the skill of the craftsmen.  Two hundred and forty five minutes of labor if he did it himself\ldots and the result would be stronger, better and more efficient if he did.  One thousand, four hundred dollars plus salaries.



Impractical.  Getting his enemies into the area would be hard.  Impossible, if they had any intelligence at all.



He dismissed the thought, but others were already flooding into place.  Him and his two Ambassadors in the offending wing, connected to nearby buildings by an arrangement of steel cables.  Not one pendulum, but seven.



One pendulum would cut the tumorous wing free.  It would swing out on the steel cables, between the two buildings.  With the right angle, it would swoop between the two nearest buildings.  The right mechanism, and one cable could come free at the right moment, allowing a change of direction.  They wouldn't even lose their balance, as the angle of the floor and centripetal force kept them steadily in place.



With attention to details, they'd even be able to step free of the platform, as though they were departing a ski lift.  The wing would then slingshot into the rubble of a nearby building, cleanly disposed of.  The Forsberg Gallery would be pulled apart, steel cut from steel by the shearing blades of the pendulums, the weight and movement of the mechanisms serving a second purpose by magnifying the damage, pulling individual pieces free of one another and setting the complete and total destruction of the building into motion.



The unseemly Forsberg Gallery would crash to the ground, with many of his enemies inside, while he and his Ambassadors watched from the point where they'd disembarked.



He loathed making messes, but cleaning up after the fact was so very satisfying, whether it was mopping up the gore or seeing the lot cleared of debris.



Thirty two minutes to draw out blueprints for the pendulums and work out the sequence needed for best effect.  Three hundred to three hundred and forty minutes of time to set it up.  He could estimate costs north of eleven thousand dollars, not counting salaries.  None of the materials were particularly expensive in and of themselves, and he had any number of businesses in his pocket where he could acquire those materials at a significant discount.



Somewhat more practical, but impossible.  He didn't have the time to set it up, not for tonight.  It made for an elegant image, if nothing else, somewhat soothing.



No sooner had he turned away from the idea of violence than other thoughts were forcing their way into his mind's eye.  The outstretching wing being transformed from an edificial cyst to a bridge, with similar connections networking the entire city, each bridge and connection point changing individual points of design into a series of \emph{gradients}.  Architectural styles and building heights would change from a stuttering, jilted progression to something \emph{flowing}, a \emph{seamless wave}–



Accord closed his eyes briefly, doing what he could to shut it out.  It didn't help.  He had a sense of the building as a whole, could imagine reconfiguring it, removing the parts that jutted out and using them to fill gaps towards the building's center mass.  He'd worked with his power to see things through the various lenses of viability: money, resources, time, personnel, but that was almost a detriment now.



He opened his eyes to search for something to take his mind off of the irritating aspect of the building's design, but he saw only glass shards, discordant in how they had fallen throughout the building.  Some had been swept out of the way by people who'd taken up residence in the Gallery, but the heaping, lumpy piles of glass, dust and debris weren't any better.  He caught a glimpse of a soggy sleeping bag and the scattered contents of a supply kit and wished he hadn't looked.



Images rifled through his mind.  A network of wires, drawn taut by a weight plunging through the elevator shaft, moving in concert to sweep the glass shards and signs of human life into the elevator shaft.  The same wires would catch his enemies, mangling them as they were cast down after the rain of glass.  Between the long fall and the thermite that could reduce the mess to a fine, clean ash, even more durable capes wouldn't be walking away.



No.  It wasn't constructive to think this way.



On the uppermost floors, plexiglass and a large volume of water mixed with a high concentration of carbon dioxide and a sudsing agent, sweeping through the building.  Staggering it, so the water from the highest floor could clean away the soap-



Rearranging the glass shards into a kaleidoscopic-



``Citrine, Othello,'' he spoke, interrupting his own train of thought.  ``Distract me.''



``I'm not so comfortable with this vantage point,'' Citrine said.  ``The climb only tires us out, and the vantage point doesn't suit any of our abilities.  It puts us in a weak position.''



``Sir,'' Othello whispered.



``\ldotsSir!'' she belatedly added.



Accord was ascending the stairs just in front of her.  It might normally be impossible, but here, it was easy: to turn and deftly slice her throat with the folded blade within his cane.  Quiet, efficient.



He stopped partway up the stair case and faced her, saw her unharmed and unhurt.  His Citrine, young, blond, wearing a goldenrod yellow evening gown and a gemstone studded mask.  Her hair was immaculately styled, her makeup flawless, with a yellow lipstick that matched her outfit without being garish.



Accord's left hand folded over the right, both resting on top of the ornate cane.



She stopped, glanced at Othello, beside her.  ``I'm sorry, sir.''



``Everything and everyone in the appropriate place,'' he said.  ``Not just in terms of physical position, but \emph{socially.  }Courtesy and acknowledgement of status are \emph{pivotal}.''



``I know, sir.  It's not an excuse, but I was tired from the walk and the climb, and I was thinking of strategy, in case we were ambushed.  I will endeavor to do better, sir.''



``We \emph{all} have to do better.  We must all strive to improve.  A step backwards is a tragic, \emph{dangerous} misstep.''



``Yes sir.''



As if he were watching himself on film, he could see himself pushing her down the stairs.  Not so steep a fall as to kill her, but the pain would enforce discipline, and the act of discipline would both help drive the point home for her and quiet his own thoughts.



But the bruises, cuts any broken bones, her inconsistent attempts at suppressing any sounds of pain as she joined him on the trek to the upper floor?  It would only make things worse.  More \emph{disorder}.



The thoughts were so sharp they were difficult to distinguish from reality.  He shifted his hold on his cane, staring into her eyes.  She still stood before him.



With just the fractional movement of his hands, there was a change in her body language.  Muscles in her neck and shoulders grew more taut, her breathing changed.  She said, ``Sir-''



``Shh,'' he said.  She fell silent.



His left hand cupped her chin, his eyes never leaving hers.  More of a reaction: her eyes flickered, moving mere milimeters as she strained to maintain eye contact.  he could feel the warmth of her breath on his wrist as she exhaled slowly, the faintest of movements against his hand as she shifted her weight to stay absolutely still.



His thumb brushed against her cheek.  Soft.  He knew she dedicated an hour every morning to caring for her skin, another hour to her hair.  Unlike hers, his gaze was unwavering, assured.  In his peripheral vision, he could see her chest rise and fall.  He wasn't a sexual creature, not in the base, animal sense.  The idea of intercourse, it didn't appeal.  The \emph{mess} of it.  But she was a thing of beauty, nonetheless.  He could appreciate her from an aesthetic standpoint.



Citrine had shifted out of place, though.  A square peg, just askew enough that it wouldn't slide into the hole designated for it.  It jarred, and it cast a pallor on everything else that was right about her.



As his fingers moved, tracing the line of her jaw, drifting to her chin, the idea of cutting her throat invaded his thoughts.  A quick, clean severing of vital flows.  He could see the lines of tension in her neck as she stretched it, striving to keep it absolutely still.



Again, though, the disorder, the \emph{disruption}.  Blood was so messy, and as much as he might relish the opportunity to take thirty minutes from his day and clean up back in a more secure area, others would see, and it would throw too many things out of balance.



There wasn't a right answer here, and it bothered him.



Thinking rationally, he knew he was irritated.  The location, even this city, they didn't suit him.  He couldn't act on that, not yet, and the resulting dissatisfaction affected how he responded to the little things.



His fingers broke contact with her chin, one by one, as he contemplated his options.  By the time his index finger had dropped away, he'd decided.



``You're my best ambassador, Citrine,'' he said.



She was breathing just a bit harder than she had been, as the tension that had drawn her entire body tight was released.  A flush touched her cheeks as she responded, ``Yes sir.''



``I don't want to lose you.''



``Yes sir, I'll do my utmost to ensure you don't have cause to.''



``Please do,'' he said.  He noted that the flush had spread down to her decolletage.  Not the result of fear or anger.  Another base emotion.  ``Citrine?''



She glanced at him.



``Calm yourself.''



``Yes sir,'' she breathed the words.



He glanced at Othello, who wore a black suit and a mask divided between alabaster white and jet black.  The man hadn't commented or flinched as Accord addressed Citrine.



Accord turned and started ascending the stairs again.  ``Quicken your paces.  I refuse to be late.''



Intrusive thoughts continued to plague him.  He'd once described it as being very similar to the sensation one experienced on a train platform, a ledge or while standing in front of fast moving traffic, that momentary urge to simply step forward, to see what might happen.



Except the thoughts were sharper, with more \emph{weight} to them, more physical than ethereal.  His power was problem solving, and every problem \emph{demanded} to be addressed. The solutions were posited whether he wanted them or not, one step and hundred-step plans alike.  And it never ended.



Every flaw needed correcting, every imbalance needed to be weighed again.  Mediocrity could be raised to greatness.



The greater the problem, the faster he could solve it.  He'd taken the time one afternoon to solve world hunger.  Six hours and twenty-six minutes with the internet and a phone on hand, and he'd been able to wrap his head around the key elements of the problem.  He'd drafted a document in the nine hours that followed, doing little more than typing and tracking down exact numbers.  A hundred and fifty pages, formatted and clear, detailing who would need to do what, and the costs therein.



It had been bare bones, with room for further documents detailing the specifics, but the basic ideas were there.  Simple, measured, undeniable.  Every major country and ruler had been accounted for, in terms of the approaches necessary to get them on board, given their particular natures and the political climate of their area.  Production, distribution, finance and logistics, all sketched out and outlined in clear, simple language.  Eighteen years, three point one trillion dollars.  Not so much money that it was impossible.  A great many moderate sacrifices from a number of people.



Even when he'd handed over the binder with the sum total of his work, his employer had been more concerned with the fact that he'd shown up late to work for his job.  His boss had barely looked at the binder before calling it impossible, then demanded Accord return to work.  A mind like his, in an office handling economic oversight within the PRT, looking for the precogs and thinkers who were trying to manipulate the markets to their own ends.



It was only one imbalance, one irregularity, but it had been an important one.  It had nagged at him, demanded resolution.  He \emph{had} to prove it was possible.



So he'd siphoned the very funds that his department was managing.  It hadn't been hard to redistribute some of the wealth that the villains and rogues were trying to manipulate.  One ambiguous evil for the sake of an undeniable good.  He covered his tracks flawlessly.



In the process, he failed to account for the full breadth of his newest coworker's talents.  Thinker powers interfered with one another, and despite his ability to work with that particular drawback, even help them to work in concert, the clairvoyant had found him out.  He'd been caught, jailed, and subsequently freed by the jailbreak specialist he'd contacted well in advance.



Here he was, years later.  Nobody he'd contacted had taken to his ideas, and government after government had failed to thoroughly read the documents he sent them.  Nobody raised the subject of his work to the United Nations or any major political body.  They were too interested in maintaining the status quo.



His plans weren't \emph{observably }closer to fruition, but he had contacts and he had wealth, and that went a long way.  He would take the slow, steady path to victory.  The binder relating to world hunger had been expanded on, with the addition of further binders to detailing the specifics.  Other sets of binders had joined it, each relating to a major issue: disease, population, government, energy, and climate.  He spent an hour and a half every morning ensuring that everything was up to date with recent changes to the economy and international politics.



The recent altercation with the Slaughterhouse Nine in Boston had been a setback, but he remained confident.  Twenty-three years to see it all through.  Twenty-three years to bring the world into order.  \emph{Everything} was a step towards those ends.



Even this, as much as the setting and the people grated.



They reached the top floor and came face to face with the Teeth.  Seven parahumans, wearing costumes that bristled with blades, spikes and spines.  They managed to wear the trophies of their defeated enemies without looking primitive.  Teeth, eyes, dessicated body parts and bones were worked into their costumes, a collective theme that promised aggression and violent retaliation for any slight.



Accord tightened his grip on his cane.  He \emph{itched} to end them.  His mind burned with hundreds of ideas on how to do it.  Traps, ploys, ways to set them against one another, or ways to use the other people in the room against them.



The Teeth didn't get in his way as he led his two ambassadors around the periphery of their group.  There were no windows, and the wind sent minuscule shards of glass dancing over the tiled floor, periodically glinting as they caught the light from the flood-lamps that were set around the room.



``Welcome, Accord,'' Tattletale greeted them.



He surveyed the group at the end of the long table.  They weren't holding back, in making a show of power.  No less than six dogs were chained in place behind them, each mutated and grown to massive size by Bitch's power.  Their number was bolstered by the addition of a massive spider and a scorpion, both wrought of black cloth.  Silk?  \emph{Skitter's} silk?



Regent stood by Imp, a costume of predominant white contrasted by a costume of black.  They seemed to be exchanging murmured words.



Bitch wore a mask that looked much like her dogs did, bearing a black jacket with thick, shaggy fur around the edges of the hood and collar.  She didn't flinch, even as one of her larger mutants growled and gnashed its teeth inches from her head.  The creature's ire was directed at Accord, not her.



Parian's style of dress had changed from the images Accord had seen in his research.  Her hair was no longer blonde, but black, her frock matching.  The white mask she wore had a crack running down one side.  She was very diminutive compared to the others, almost demure with the way she sat at one side of the table, hands folded, as though she didn't want to be a part of this.



Tattletale, by contrast, was seated on the cloth scorpion, just beside a large monitor.  She was cavalier, her hair wind-tousled, disrespectful by her very body language, sitting askew.



He had to work to ignore her.  He turned his attention to the figures at the head of the table.  Grue stood behind the chair, one hand set on the backrest, a demonic visage wreathed in absolute darkness. Skitter sat at the end, backed by her forces, looking over the room.  Bugs swarmed her from the shoulders down, but Accord could note a shawl and hints of protective armor.  Neither the yellow lenses of her mask or the expanse of black cloth that covered her face gave any indication of her mood or expression.  Either the images that he'd seen had been misleading, or she'd done some work to her mask, making the mandible-like sections of armor that ran forward from her jawline sharper and more pronounced.



Dismissing Tattletale's greeting, Accord spoke to Skitter, ``We finally meet.  Good evening.''



``Good evening,'' she said, her voice augmented by the accompanying buzzes and drones of countless bugs in the area.  ``Have a seat.''



He took a seat midway down the length of the twelve-foot table, and his ambassadors sat on either side of him.



The Fallen must not have been terribly far behind him, as they arrived less than a minute after he did.  Valefor and Eligos.



Valefor wore a delicate-looking mask without eye-holes: a woman's upper face with closed eyes.  Beneath the mask, he had a sly, perpetual smirk with tattoos that colored his lips black and extended from the corners.  The ink depicted fangs poking from thin lips that nearly reached his jaw, the points alternating up and down.  His costume was almost effeminate, with white and silver feathers featuring heavily on flowing white clothes that clung to his narrow body, including a corset that drew his waist in.



The costume was meant to invoke images of the Simurgh, no doubt.  Crass.  Eligos' costume wasn't so fine, suited more for a brawl, but it, too, conjured up thoughts of an Endbringer: the Behemoth.  Obsidian horns that swooped back over his head, heavy armor that resembled rhino hide in texture and claws built into his gloves.



``Valefor, Eligos, members of the Teeth, now that we're all here, I'll ask that you take a seat,'' Skitter said.



``Why should we listen to you?'' Valefor asked, his voice was incongruous with his outfit, bearing a slight southern twang.  He leaned over one chair, his arms folded over the backrest, taunting.



``It's customary for there to be violent retaliation if someone causes trouble at a meeting like this,'' Skitter said.  ``Usually involving every other party that's present.''



``I'm not saying I'm intending to cause trouble,'' Valefor said.  ``I'm wondering why we should follow the \emph{schoolgirl}.  I'm sure everyone here saw the news.  Did \emph{you} see the news, Butcher?''



``Yes,'' the leader of the Teeth answered.  A woman stepped out of the midst of the group of Teeth.  She was elegant, long necked and long-limbed, with her hair tied up in a high ponytail.  Her mask and armor had an Asian style to it, though the costume were studded and trimmed with a number of wickedly barbed blades.  More incongruous, there were three bleached skulls strung to one another and hanging around one shoulder.



The costume, it was asymmetrical, lacking harmony, trying to do too many things at once.  The samurai, the headhunter, the bloodletter.  None of it fit the title she wore: Butcher.



Images flickered through Accord's mind.  Ways to obliterate both costume and wearer. More difficult than it seemed, given just who she was.



As if to punctuate Accord's line of thinking, she effortlessly lifted a gatling gun and set it down on the end of the table.  The sheer mass of the weapon was imposing enough that Accord momentarily wondered if the other end of the long wooden table would lift off the ground.



The woman very deliberately refused the offer to sit.  She'd spoken only one word, but managed to convey a great deal with her actions.



``Very embarrassing,'' Valefor mused aloud.  ``Really, I don't see why you should get to sit at the head of the table.  A sixteen year old girl, a victim of bullying, it doesn't conjure up the most imposing image, does it?''



``If everyone agreed to suspend the usual rules, I would be more than happy to go head to head with your group,'' Skitter replied.



``Of course you would.  You outnumber us.''



``Just me,'' Skitter answered him.



``That so?''  Valefor smiled, considering.



Accord surveyed the situation.  Valefor was a stranger, less in terms of his ability to hide, and more in his ability to engage in subterfuge.  He had only to look on a target with his naked eye, and the fight was over.  It was no small wonder, really, that he'd styled himself after the Simurgh.  The effect was all too similar, in how the victim was often unaware of what had happened until it was too late.



Yet Skitter didn't seem to mind.  Was it a decoy?  An empty costume?  No.



A trap?



Accord studied the area around Valefor.  What would he do, with her abilities?



He saw it: almost invisible, except where the light caught it at the right angle.  Threads, surrounding Valefor, trailing from his corset, his elbows and knees.



They were all trailing in the direction of the window.  If they were pulled taut, Valefor would be dragged outside.  Depending on how well they held, he'd either dangle or fall to the street below.



``Valefor,'' Accord spoke, the layers of his mask shifting to emulate his smile, ``Trust me when I say you already lost the fight.''



``Is that so?''



``I won't spoil the conclusion if you're eager to see this through.  One less threat to worry about.  But if I may offer my own opinion, I think the response she gave, given the situation, was eminently reasonable.  I \emph{gained} respect for her, seeing how it unfolded.''



``Then you're a fool.''



``Regardless, I won't condone fighting here.  It sets a bad precedent.''



``Yes,'' Butcher said.



Valefor frowned.



``That's that, then,'' Skitter said.



Accord studied her.  He could see her swarm in the shadows behind the floodlights, moving in anticipation of a fight, no doubt.  Their presence nettled him almost as badly as if they'd been physically crawling on him.  They were all of the issues he'd had with the glass, but they were \emph{alive}.  He knew he could make them stop, make them go away, simply by giving an order to his ambassadors.  Not that it was a possibility.



He glanced at Skitter.  ``I think you and I both know you'd win the fight.  But how final would the outcome be?  You're in the seat of power.  More villains will arrive with every passing day.  Are you prepared to kill?''



``Is this some kind of head game?'' Valefor asked.



``It isn't any \emph{manner} of head game,'' Accord responded.  ``I'm curious.  Her response would shed a great deal of light on the discussion tonight.''



``Yes,'' Skitter gave her belated response.  ``But I'd like to keep to the unwritten rules, as abused as they have been, lately.  Killing should be a last resort.''



``I see.''  \emph{She has some other trap on hand?}  The bugs at the edge of the room?  ``Can I ask if- no, wait.  Don't tell me.  I'll enjoy it more if I discover it for myself.''



``Very well.  Now, if everyone would be seated, we can begin,'' Skitter said, resting both elbows on the table.  



It wasn't quite straight, Accord noted.  The table was askew, in relation to the rest of the room.  Solutions flickered through his mind's eye, ranging from ones as simple as standing to push the table into a proper position to a flat-faced wrecking ball that could slam into the building's side.



No, he had to focus.  He could distract himself by figuring out Skitter's contingency plans.



Butcher seemed to come to a decision, but that was normal for her, to take some time, ruminate.  To \emph{discuss}, for lack of a better word.  She sat at the end of the table opposite Skitter.  She was tall enough to be seen head and shoulders over the massive gun.  Her followers didn't sit, but stood in a half-circle around her, a mirror to Skitter's own group.



``Valefor,'' Skitter spoke, and her voice was more ominous, hinting at the sheer number of bugs lurking at the edges of the room, ``Either take a seat or leave.''



Valefor glanced over the room, then shrugged, as if he didn't care anymore, sitting.  Eligos followed his cue.



And Accord realized Skitter's contingency plan in the next instant.  Silk wasn't just attached to Valefor, to \emph{him}, even.  She'd connected silk to the furniture.



The table.  She could drag the table with the silk lines, each laid out to fit in the gaps between tiles, nearly invisible.  In doing so, she'd sandwich any one group between the table and a wall, or leave them clinging for a grip, almost falling.



How would she drag it?  Another mutant dog?  Some counterweight?



Regardless of the answer, Accord felt oddly pleased with himself.  The danger posed by this trap didn't even concern him.



``Let's talk business,'' Skitter said.  ``Whether you like it or not, the Undersiders have prior claim on this city.''



``A matter of a week and a half,'' Valefor said.



``Prior claim,'' Skitter repeated herself.  ``We have rules, and if you bend or break these rules, we'll be forced to act.''



``I've already discussed your rules with Tattletale,'' Accord said.



``You had your chance to accept the terms we were offering\emph{ then}.  Now the rules we're stipulating have changed.  No killing.  Cross that line and we kill you.  Several members of our team are capable of doing that without you knowing we're anywhere nearby.  If you're lucky, Imp slits your throat with you none the wiser, or Regent has one of your underlings stab you in the back, and you go quick.  If you're unlucky, Bitch's dogs tear you to shreds, and it's a long, drawn out, painful process.  If you're \emph{very} unlucky, you get the worst of both worlds, and you deal with \emph{me}.''



``What if there's someone that has to die?'' Valefor asked.  ``Sometimes killing is necessary.''



``You come to me.  I decide,'' Skitter said.



``There's no new detail here,'' Accord said.  ``Tattletale outlined much the same thing, though with less in the way of threats.''



``I'm not even close to done.  Property.  We \emph{will} find out about any territory you acquire.  Whatever you pay for the land, you pay us a third.  That includes the cost of buying the land itself, rent and taxes.  If you're not paying property taxes or rent, we still expect an appropriate amount.''



``Expensive,'' Accord said.



``You could have accepted our earlier offer,'' Skitter replied.  ``If you want out from under that particular constraint, any of you may fold your organizations into ours, coming under our direct authority.''



``This is a passive takeover, then,'' Accord said.  ``You intend to put the squeeze on us until we cave.''



``I am very, \emph{very} tired of people telling me what I intend,'' Skitter answered him.  ``Our territory borders are marked with our individual signatures.  Traffic in anything illegal or harm someone within any of these areas, and we retaliate.  Target any of us, and we retaliate as a whole.''



``It doesn't sound like it leaves us much elbow room,'' Accord replied.  ``I have yet to see an area that wasn't already marked as being in one territory or another.''



``Then you grasp my meaning.'' Skitter added, ``My next point: during any Endbringer event, or the possible incident at the end of the world, you send half of your powered membership or three members to assist, whichever is more.''



``This is bordering on the ridiculous,'' Valefor said.  ``You expect \emph{us} to fight the Endbringers?''



``You?  No.''



``You're picking a fight,'' Valefor said.



``I'm giving each of you the option of obeying, leaving or fighting,'' Skitter said.  ``The Ambassadors will accept the deal as posed.  They won't like it, Accord may even hate me, because of my powers and my less predictable nature, but they'll accept.''



``Is that so?'' Accord asked.



``Yes.  You'll do it because you have resources that you can use to leverage what unfolds when they've finished scouting the other side of the portal and open it up for business.  You wouldn't come all the way here and then leave because you didn't like the terms.''



``There are the other options.''



``Fighting us?  You have only two underlings that survived the attack in Boston.  As strong as they are, you're not equipped to fight.  You'll join us because it's the fastest route to get what you \emph{really} want.''



\emph{Ah,} Accord thought.  \emph{Tattletale filled her in.}



It made life a little easier, and a little harder, in very different ways.



Skitter leaned back, one hand resting on the table.  ``What was it you said to Tattletale?  Everyone and everything has a place?''



``More or less.''



``Your place isn't on a battlefield, opposite the Undersiders.  It's in this city, building an infrastructure and gathering resources for your long term plans.  You'll accept an expensive rent and a limitation on criminal activity for that very reason.''



``You would have me risk good help on fruitless fights against immortal killing machines,'' Accord said.



``That too,'' Skitter replied.  ``I don't expect the Fallen will accept the terms, with the restriction about fighting Endbringers, but I doubt they're long for this city anyways.''



Valefor stood from the table.  Eligos joined him.  Together, they strode from the room, silent.



``That was a touch rash,'' Accord commented, ``insulting them.''



``I wasn't lying.  Imp and Haven will handle them soon.''



``Valefor is more cunning than you'd assume.  An arrogant young man, impetuous and immature, but history suggests he's rather cunning when he puts his mind to something.''



``Not a concern,'' Skitter said.



``If you say so.''



Skitter turned her attention to the other leader.  ``Butcher?''



``No,'' the woman replied, standing from the table.



``I didn't think so.  Do you have any other business you'd like to bring up, while we're all here?''



``You die,'' Butcher said.  ``You can't kill me.  I will win.''



With that, her longest statement yet, she turned and walked away.



``Not good enemies to have,'' Accord commented.  It was just his group and the Undersiders now.



``We'll manage.''



``The first Butcher had super strength, durability, and the ability to inflict enough pain at a distance that his enemies went into cardiac arrest.  His other powers only became evident later.  He was killed by a subordinate, and the man who would later be known as Butcher Two inherited a fraction of his powers and a share of his consciousness.''



``Butcher Three inherited it too, along with a share of Two's powers and consciousness,'' Tattletale said.  ``He was a hero, though.''



Accord rankled at the fact that she'd spoken out of turn.  Her voice rang in his ears, as though each syllable were the echoing toll of a bell, growing louder with each iteration.  Out of turn, out of sync, out of place.



He bit his tongue.  ``Yes.  And the two voices in the hero's head worked together to drive him mad.  He was gone from this world well before he died in battle.  The Teeth reclaimed the power, and the legacy has largely remained within the group since, each successor inherting powers of the ones before.  The voices and consciousnesses only work with \emph{rightful} heirs, members of their group who challenge the leader and beat him in a fair match.''



``Which one is this?'' Regent asked.



``Fourteen,'' Tattletale said.



``This one's number \emph{fourteen}?'' Regent asked.  ``Which means she's got thirteen sets of powers?''



\emph{Another one, speaking out of turn}, Accord thought.



Citrine was giving him a sidelong glance.  He met her eyes, shook his head fractionally.



Tattletale answered, ``Only a small share of each power.  Don't forget she's got thirteen voices in her head, giving her advice and helping her work stuff out, and all the powers she brought to the table, besides.  Her attacks don't miss.  She imbues them with an effect which means they bend space so they strike her target,  Bullets turn in midair, swords curve, all means she's pretty much guaranteed to hit you if her attack reaches far enough.''



She hopped down from the scorpion's head and walked around the table until she was opposite Accord.



One by one, the Undersiders who'd been standing behind Skitter found seats.  The other groups had left, and they were making themselves more at home, now.  Regent put his boots on the table, right in front of Imp, who pushed them away.



\emph{Overly familiar.  Presumptuous}.



Accord closed his eyes for a moment.  The table was unbalanced now, in a metaphorical sense, but it felt very real.  ``I don't recall anyone giving you leave to sit.''



Tattletale raised her eyebrows.  ``I don't recall anyone giving you permission to complain.  Our territory, our house, our rules.''



\emph{I could kill you.  Car bombs, other traps.  I could manipulate the heroes into going after you.  When I direct my ambassadors, they win their fights.  You'd break in the face of what I could do, the pressure I could inflict, everything and everyone in the world suddenly a threat, with me pulling the strings.  }



He drew in a deep breath.  Too much at stake, to say such things.  In his most patient tone, as though he were speaking to a well meaning but misguided eight year old, he explained, ``I'm talking about the way things are \emph{meant} to be, Tattletale, understand?''



Tattletale bristled as though he'd slapped her.



``Enough,'' Skitter said.  Her voice was quiet.



The silence that followed was both surprising and relieving.  She had control over her subordinates.  Good.  It took a measure of talent to exert control over such disturbed individuals.



He studied the girl.  She was composed, despite the fact that less than twelve hours had passed since her identity had been revealed to the world.  And her bugs\ldots it had grated how disordered they had been, but now that he was looking at the ones she wore like a second layer of clothing, he could see how they were ordered, all in formation.



Skitter was calm, collected, reasonable but willing to act with a heavy hand when needed.  Clever.  She thought at the scale necessary for a true leader.



``Do you accept the deal?'' Skitter asked.  ``Best if I ask now, because your answer dictates the tone of the conversation that follows.''



``I accept,'' he replied.  She was right: he really had no choice in the matter.  He'd dealt with worse deals and worse circumstances before.  ``I suspect there will be friction, and we will have our disagreements, but we'll be able to find a common ground.  You and I are very similar people.''



She didn't reply.  The silence yawned, and his fingertips twitched involuntarily, dangerously close to the trigger that would turn his cane into a weapon.



``In saying that,'' he said, doing his best to remain level, ``I was inviting a response.''



``And I was taking a second to think before giving it,'' she responded.



\emph{Starting a sentence with a conjunction}.  He grit his teeth and smiled, his mask moving to emulate the expression.  ``Beg pardon.''



``Let's talk about details,'' Skitter said.



\blacksquare



\emph{The city is too dirty. }\emph{Too disordered}.  The thoughts were intruding again, oppressive, insistent.  They were at the point where they were repeating, cycling back on one another.  He'd have to do something to break the cycle.  It could be time spent at a workbench, sorting out the projects in his binders or eliminating some of the more chaotic elements.



Murder was out, but there were other options.  He'd sent capes to the Y\`{a}ngb\v{a}n before.  It was more constructive than killing.  Cleaner.  It also built relationships with the C.U.I..



``Talk,'' he said, after too many long minutes of silence.



``We can take them, sir,'' Othello said.  ``Any one group, we could handle, but not two groups at once.''



``I agree,'' Accord said.  ``Do you think you could handle them if things went sour?''



``With little trouble, sir.  The only ones I'd wonder about are Tattletale, Imp, Valefor and Fourteen,'' Othello replied.



``Imp and Valefor\ldots your stranger powers against theirs makes for a troublesome fight.  Imp is the one I would worry about first.  Unpredictable, impossible to track.''



``I'm suspicious my power cancels hers out, sir.  My other self saw her get close to Butcher.  I think she had a weapon.''



``Interesting.  Citrine?''



``I don't know, sir.  Forgive my saying so, but a lot of people have thought they could handle the Undersiders, and they were wrong.  I don't know how my power would interact with theirs.''



``Very true.  Sensible.  I'll need to recruit, regardless of whether we encounter them.  Focus on the Teeth and the Fallen for the time being.''



``Yes sir,'' the pair echoed him.



\emph{Skitter and Tattletale}, he thought.  They were the real issues for \emph{him}.  Tattletale's power might have seemed similar to his own, but it was almost the inverse.  He'd heard himself described as falling somewhere in between a thinker and a tinker, and perhaps that was apt.  It was how he applied his power, starting with the end result and building backwards, and the designs that he fashioned that were so tinker-like.  But his real ability was as a thinker, involving planning, awareness and ideas beyond the reach of the unpowered.



He hoped it wouldn't come to that, but he had to plan for every contingency.



They'd reached their accomodations, a newly built office building.  He owned the two uppermost floors, and was buying the floors beneath as the owners agreed to the sales.  Soon he would have it set up his way, with escape routes and traps to target his enemies.



``Othello,'' he said.



``Yes sir?''



``Send the five first tier employees with the best grades to my room.  I expect them in fifteen minutes.''



``Of course, sir.''



``Once you're done, retire for the evening.  Rest well,'' he said.  ``There are big things on the horizon.''



``Yes sir,'' the two ambassadors echoed him.



Only two.  It wasn't enough.



He settled in his room.  Too much of the furniture was pre-made.  He preferred things he had made himself.  Cleaner, simpler.  He knew where it had all come from, knew how it was put together.  Accomodations he had crafted himself were as soothing as the outside world wasn't.



The five employees arrived right on time.  Satisfactory.  He opened the door to his room and invited them in.  Three men, two women, immaculate, all in proper business attire.



His vetting process was strict, and each step up the ladder required both his invitation and the employee's acceptance.  Each step required them to prove their worth, to face progressively more stress and heavier workloads, and to hold themselves up to his increasingly exacting standards of perfection.



It might have made for reality television, if it weren't for the blood that was shed along the way.  Theirs and others.



``You are being promoted,'' he said.  ``After tomorrow, you will be my ambassadors, my representatives to the rest of the world.''



The displays of emotion were well hidden, but they were there.  They were pleased.



``That is all.''



Wordless, the five marched out of his room.



Withdrawing his cell phone, Accord dialed a long distance number.



He smiled a little at that.  He wasn't much for humor, but it had its places.



The ringing stopped, but there was no voice on the other end.



``Accord.  Brockton Bay.''



The doorway opened at one end of his room.  His hair stirred as air pressure equalized between the two planes.



The Number Man stood on the other side, in the white hallway with white walls.



``Five vials.  Of the same caliber as the last set, same price.''



``Done,'' The Number Man said.  ``Where do we stand?''



``It's promising, but I wouldn't make any guarantees.''



``Of course.  Everything's progressing according to plan, then?''



Accord nodded, once.  ``As well as we might hope.  We lost Coil, but the Undersiders may serve as a model in his absence.''



``Good to know.  I'll inform the Doctor.''



The gateway closed.  Accord sat down on the end of the bed, then lay back, staring at the ceiling.



Coil had been the focus of the test, unaware.  The man had also been Accord's friend, the one who'd sold him the PRT databases.  His death had been a tragic thing, on many levels.  There were few men Accord considered worthy of being his friend.



Now it hinged on the Undersiders.  They'd taken up Coil's legacy, after a fashion, and just like Coil, their ambitions fell in line with Cauldron's.  The organization's hopes rode on them and their decisions.  \emph{Accord's} hopes rode on them: his twenty-three year plan, saving the world from the worst kind of disorder.  In the end, they were responsible for billions.



Not that he could tell them or change his actions in respect to them.  It would defeat the point.



Everything and everyone had their respective places in the grand scheme of things.  For one sixteen year old, the decisions she made in the immediate future would have more impact than she imagined.



It all came down to whether she could embrace this new role, and whether the city could embrace her in turn.



Accord drifted off to sleep, his weary mind grateful from the respite from the endless assault.





