





``This is exactly what I was talking about.  She's a dangerous influence.''



``She's a sixteen year old girl with strong opinions, Wilkins,'' Armstrong answered.  ``Nothing more.  She holds onto those opinions and her core worldview, and vulnerable people get caught up in her momentum.  Cult leaders will do the same thing, only it's \emph{purposeful} in their case.  Get people tired, get people worn out, scared and hungry, and then give them someone with \emph{presence} to give them support.''



``You're saying she's an accidental cult leader?''



``She's in a position where it's very easy to sway others.  A lot of the parahumans out there fit the criteria I'm talking about,'' Armstrong said.  He glanced at Glenn, who looked distinctly unhappy.  ``So, apparently, does our staff.''



``I think you're off target,'' I said.  ``You're talking about Foil, I get it, and Parian, and now the Chicago Wards and Glenn.  But all of the decisions they made were when I wasn't anywhere near them.  Unless you're implying I have some sort of mind control.''



``No,'' Armstrong told me.  He didn't fit his name; he looked more like my dad than anyone, though he had a peculiarly prominent jaw and a forehead that made it look like he was perpetually glaring.  ``It doesn't matter if they're near you.  The message and the idea stays with them even after they leave your presence.''



``Tecton just wanted someone to call the shots, to replace Raymancer,'' I said.  He was defending me, but it wasn't \emph{helping}.



``We saw the video,'' Director Wilkins said.  ``We know what he said.  I think it's best if you stop talking.''



I bit my lip and turned my eyes to the table.



``Well,'' Glenn said.  ``What's done is done.  Can I suggest that perhaps, because it's been a long day, we should retire?  All of us will still be here in the morning.''



``It sounds like a good idea,'' Armstrong said.  One or two heads around the table nodded.



``We're going to handle this tonight,'' Wilkins said.



``While the girl's so tired she could fall asleep sitting up,'' Glenn observed.  ``Or is it that you want to resolve this while Chevalier is in the hospital?''



``Chevalier doesn't matter,'' Wilkins said.  ``This is PRT business.''



``I agree.  His input would be appreciated, if he was in a state to give it, but it's ultimately not his decision,'' the Washington director said.  He reminded me of Piggot, but he wasn't fat.    Heavy, but not fat like she'd been.  It was more the way he held himself, his tone and approach.  His graying hair was cropped close, and he had a combination of paler skin and dark circles under his eyes that made me think of a corpse.  Director West.



``We lose nothing by waiting,'' Glenn said, calm, unflappable.  I'd seen that confidence before, in people who'd had nothing to lose.  \emph{I'd} had that confidence before.



``We lose time.  If we're going to respond to the press and the public, we need to act sooner than later.''



``My concern\ldots'' a woman said, drawing out the thought, ``Is that her actions go against the \emph{spirit} of the PRT and the groups under the PRT's umbrella.  Conspiring with a known terrorist, \emph{betraying the truce}, even, for a subtle advantage in dealing with that terrorist, returning to her old team against all terms of her probation, rejecting orders, and taking reckless risks with PRT personnel, getting two injured.  A longstanding goal of the PRT has been to reassure the public, and this only paints heroes as something dangerous.''



I already didn't like her.  I wasn't even sure what city she was from.



``That doesn't even include the fact that this leak shows capes going all out.  When the joy at the victory wears off, people are going to look at the footage and wonder if they're in danger,'' West said.



\emph{We won}, I thought.  \emph{We beat him, and you're quibbling over details}.



Why were they doing this?  Why were they so intent on railroading me?  Screwing me over?



These guys, or some of them, were the old guard.  Defenders of the status quo.  Tagg would have fit into this little cadre.



Maybe that was part of the reason.



``--Birdcage.''



The word hung in the air.



I snapped to attention, fully awake in an instant.  I had to take a second to look at the faces of the people around the table before I realized who'd said it.  Armstrong, the man who'd been my advocate an instant ago.



``A little extreme,'' West said.



``The next few fights are going to be crucial.  Every time the Endbringers come, there are major losses.  We lose good capes.  Others step in, but they don't have the experience or the organization, so we lose more.  New Delhi was very nearly the culmination of that.''



``We won New Delhi.''



``\emph{We} lost.  \emph{Scion} won,'' Armstrong responded.  ``Participation will be up for the next fight.  Let's \emph{use} that.  We bolster the numbers further, by tapping the Birdcage.  There are powerful capes in there, and some are cooperative.''



\emph{Oh.  They aren't talking about me}.



``And if they start wreaking havoc afterward?  Or turn on us?''



``We can be select about it.  Dragon's willing to give us a searchable database of all of the conversation and behavior records within the Birdcage.''



I raised my head at that.  ``Dragon's alive?''



``She got in contact with us a short while ago.''



I nodded.  I felt a little dazed, confused.  Too much in a short time.  I was reaching the point where I wasn't sure I'd be able to take it all in.



``It's not worth it,'' West said.



``A moderate risk for a chance to save hundreds, thousands, even millions of lives,'' Armstrong said.



``How many lives do we lose because of the monsters we set free?''  West retorted.  ``Those criminals were put there for a \emph{reason}.''



``At first,'' Armstrong said.  ``But the rationale for indefinite detention has been getting weaker, and the number of capes going in has been increasing.  I--''



``It's not going to happen, Armstrong,'' West cut him off.



Armstrong deflated a little, settling back in his chair.



``The media is already reaching out to us to ask for interviews with Weaver,'' one of the other Directors said.  ``They love her or hate her, but this won't die down anytime soon.''



``Primacy effect,'' West said, frowning.  ``That video is going to be the first thing people will think about when they think about people in the field during an Endbringer attack.''



``So we drown it,'' the woman from before said.  ``Release the footage we held back, footage with a more favorable effect on us.  Weaver gets lost in the shuffle, and we quietly address the unbecoming conduct.''



\emph{We won, you bastards}.  I clenched my fists beneath the table.



``Address how?''



``It's a violation of her probationary membership.  She's off the team for the time being, if not permanently.  She fulfills the remainder of her sentence, then remains in our custody as a consult.  ''



I noticed that my bugs were acting of their own volition, treating this as a crisis scenario.  They were massing, and they were winding silk threads around the PRT uniforms that guarded the room, around the containment foam sprayers and guns that they held.



I'd missed the Undersiders, hated that I wasn't there with them as they said goodbye to Regent.  Part of the reason I'd become a hero had been to reconnect with my dad, but the gap seemed too wide.  I'd killed, and he'd seen me kill.  He was afraid of me.



It would be \emph{easy} to disable the PRT uniforms, attack the directors and simply make my way to Brockton Bay.  I could patch things up with Grue, help Rachel, ensure that Imp didn't go to a dark place.



But it wouldn't get me anywhere.



He wanted to play hardball?  I'd play hard in return.  I turned my attention to my swarm for a moment.



``I think you're underestimating how badly the public would react if Weaver was punished,'' Glenn said.



``We're facing a lose-lose situation, Mr. Chambers,'' Chief Director West said.  ``We cut our losses, take a hit in PR, but we can continue operating as we need to.  So long as it's quiet, she goes to prison and doesn't go out on another big excursion, I don't think anyone's about to make a big deal of it.''



\emph{\ldots{}make a big deal of it. } I turned the words around in my head.  Manipulating the media, manipulating the local capes.  Damn.  I'd had high hopes for Chevalier's new Protectorate, but it didn't seem to extend to the \emph{PRT}.



``We can deflect,'' the woman from before said.  ``Raise another issue, change the focus of the public.''



``Not so easy,'' Glenn said.  ``It's been done too often in the past.  They're watching for it, even anticipating it.''



``But the majority won't be,'' she responded.  She turned to Director West.  ``The alert, educated minority will complain, but they won't achieve anything meaningful.  They never do.''



``I'm inclined to agree,'' Director West said.  ``It's not pretty, but it'll suffice.''



``\emph{Why}?'' I asked.  ``You can't deny I helped.  I didn't deliver a serious blow, but I helped to coordinate, I had ideas, I used them.''



``There's other smart capes out there,'' a man said.  He didn't give me the impression of a PRT director.  Another staff member?



``I did a lot of good, and you're railroading me.  Is it because you're losing control of things and I make an easy target?  Because you're afraid of me?''



``Because you're consistently unpredictable.  Unreliable.  We set rules and you break them,'' West told me.



``Rules don't generally apply during an Endbringer attack,'' I said.  ``The only thing that matters is taking the motherfucker down.  We did.''



``I'm inclined to agree,'' Armstrong said.  ``This is going a step too far.  She did well.''



A few heads nodded around the table, but they didn't have the majority, and they didn't have the clout that Chief Director West did.  Glenn had spoken of a fifty-fifty split in the reactions, and he was more or less on target.  But the power held by the people who were standing up for me was nothing compared to the clout the others had.



``This is beyond the Endbringer attack.  It's overall conduct,'' the woman at the far end of the table said.



``When? Can you name incidents?  Beyond the Endbringer attack?''  I challenged her.



``Spiders in the less traveled areas of the prison,'' West told me.



\emph{Spiders in the prison.  Shit}.



I felt myself deflate a little, but I managed to keep my face straight.  ``If there are any, they're eggs that recently hatched.''



``And the costume?  A weave of silk cloth hidden out of sight.''



\emph{Damn}.



``That predated my discussion with the Warden,'' I lied.  ``I got rid of the spiders, moved on.''



``You could have reported it.''



``That an abandoned time-killing project was stuck in behind some pipes?  Why?''



``Because \emph{this} happens.  There's no reason to believe you.''



I clenched my fists.



``You're dangerous, Taylor Hebert.  Unpredictable.  You're deceptive, clever enough to come up with tricks, but not clever enough to stick to the straight and narrow from the beginning.  Armstrong said it himself.  You're good at manipulating people.''



\emph{\ldots{}Manipulating people}, I thought.  Not as good as I wanted to be.



Armstrong spoke up, ``You're twisting my words, West.  I said she wa\emph{s }well\emph{ situated }for interacting with vulnerable people, and stalwart enough in her own worldview that others can get swept up in her flow.''



``Regardless.  Ms. Hebert was right about one thing.  It's late.  It's been an emotionally exhausting day.''



``Physically exhausting too,'' I said, not taking my eyes off the Chief Director.  ``You know, running around, fighting Behemoth while you guys sit in your--''



Glenn shifted one leg under the table, pressing it against mine.  A nudge, not overt.



I stopped.



My power crackled at the edge of my attention.  My bugs were moving again, without any direct instructions from me.  I reined them in, and then distributed them through the building.  Was there someone I could contact?  Something I could communicate to the right person, to change what was happening here?



West ignored my comment, turning his attention to Glenn.  ``Mr. Chambers, you're relieved of duty.  You likely knew this already.''



``I understand,'' Glenn said.



``We'll discuss on our own whether we need to press charges.''



\emph{\ldots{}Press charges.}  Bastards.



``Okay,'' Glenn said.



West met my eyes.  ``Taylor Hebert, you violated the terms of your probation.  You'll return to Gardener tonight, and you'll carry out the rest of your sentence.  Your test run with the Wards teams is over.  Offer rescinded.  Provided you do not talk to the media, we stop there.  We'll talk to you when you turn eighteen, to see about plans for the future.''



``This is a mistake,'' Glenn said.  ``Chevalier had a number of plans, and you're unraveling them.''



``Naturally, Mr. Chambers.  We're aware of the thrust of those plans.  Recruiting villains.  A darker, edgier Protectorate.  Provided he keeps to the rules, we're willing to let that be.  But with the \emph{administration}, the underlying framework that makes his teams possible, we have to maintain a balance, keep the public and the President happy.  He won't have our assistance.''



\emph{\ldots{}He won't have our assistance}, I thought.



I heard the words, and my bugs spoke them.  Every bug, within the building, repeated him, verbatim.  The good, the bad, the details that damned me.  It wasn't a question of finding the right person, or saying the right thing.  It was everyone, saying \emph{everything}.



In that manner, my bugs repeated it to staff members, to the Chicago Wards, and to the Protectorate members who'd accompanied their Directors here.  It was too late for reporters to be around, but I didn't deny the possibility.



Tens of thousands of bugs speaking words at a sound barely above a whisper, louder in places where more people congregated.



Dispatch and Exalt were the first to make their way to our floor.  They entered the room without knocking.



I met Dispatch's eyes.  Not the rescuer I'd hoped for.  We'd worked together, but he'd disliked me from the outset.



``Dispatch?''  West asked.



Dispatch didn't reply right away.  He glared, and it wasn't at me.  It was at the Director.



``We've been listening,'' Exalt said.



``\emph{Listening}?''



``You've been bugged,'' Dispatch said.  ``Only the bugs are the ones outside.  They've been talking.  Reciting.''



I could see Chief Director West's eyes narrow as he looked at me.  He would be replaying the conversation in his head, trying to figure out if he had said anything damning.



``No guarantee she's telling the truth,'' West said.



``Provided he keeps to the rules, we're willing to let that be,'' Dispatch said.  ``Spiders in the back areas of the prison.''



``Yes,'' Director Armstrong said.  ``That's accurate.  I can't speak to particulars or the little details, though.''



``I repeated everything verbatim,'' I confirmed.



``The goings-on of this meeting are confidential,'' Director West said.



``Nobody told me that,'' I answered.  ``It doesn't matter.  I violated my probation anyways, apparently.''



``Anything goes against Endbringers,'' Tecton said, from the hallway.  He'd just arrived with Grace and Annex beside him.  ``We wouldn't have done half as well if it wasn't for her.''



``Tell that to Kismet,'' one of West's flunkies commented.  ``Or Particulate.  You don't really want her on your team.  Not when she's going to stab you in the back for a better margin of victory.''



``I \emph{do},'' Tecton said.  ``All of us do.  We watched the video together.  We talked about it.  Kismet made a mistake.  As far as Particulate, we looked him up.  He's reckless, dangerous.  Not the best way she could have handled it, but it worked.''



West didn't take his eyes off me.  ``Even if we ignored everything else, this kind of behavior, it's--''



``It's exactly what Chevalier wanted,'' I said.  My eyes dropped to the table.  I didn't meet his gaze, didn't try to engage the visitors.  ``Open, honest.  Exposing the rot at the center.''



``You're saying you're not rotten,'' the woman at the end of the table said, almost mocking.



``Maybe I am,'' I told her.  ``I'm not all good, not all bad.  I'm just\ldots getting by.  Doing what I can, not holding back against enemies who don't deserve it.  And under Chevalier's system, Glenn's system, I guess I'm revealing all of that stuff we usually keep hidden, and it's up to others to make the call whether they can roll with it or not.  Up to the public, my potential teammates.''



``Honestly,'' Tecton said, ``If you're going to lock her up after all this, you can consider me done.  You're going to undermine Chevalier, when what he's doing \emph{worked}?  I'm gone.''



Here and there, there were murmurs of agreement.



There was a very long pause.



``Weaver,'' Director West said.



I met his eyes again.  I could see the \emph{hate}.



``You'll make your way to Chicago at the end of the week, and provided everything goes well, you will be a member of the team.  If you're wise, you won't take interviews, and you won't take any action that draws attention to you.''



I drew in a deep breath, then nodded.



``You'll wear a tracking device at all times, and any time you leave the defined area within the Chicago headquarters, you'll have an escort, a longstanding member of the team in your company at all times.''



``Okay,'' I said.



``See to it that you follow these rules.  You've got the backing of the heroes here, \emph{maybe} you've got the public's favor, but we \emph{will} remove you if you give us an excuse.''



``I understand,'' I said, suddenly very weary.



Beside me, Glenn stood from his chair.  I took his cue.



The PRT uniforms stepped out of the doorway, where they'd been barring the small crowd access.  We made our exit, joining the Wards and PRT staff members.



``Weaver,'' the Chief Director called out.



I turned around.



``You didn't make any allies in this room today.''



``I think you were my enemies before we even met,'' I said.  ``You'd never have given me the chance to be your ally.''



``You're wrong.''



I shrugged, then turned to walk away.



Tecton gave me a nod as I approached.



``Thank you,'' I said.



``Not a problem,'' he said.  ``You kept us alive, I figure we owe you one.''



``I don't think you owe me much, but I'm not complaining,'' I said.



``We should go.  We were in the middle of something.  See you soon, I hope?''



``Yeah,'' I answered.



When they'd broken away, it was Glenn and I, together.



``That was foolish,'' Glenn commented.



``They wouldn't have given us any slack.  Nothing we could have said or done would have changed the outcome, unless we attacked from a different angle.''



``There's a habit some people have,'' Glenn said, ``Where they divide people into enemies and allies.  It's in your records, as a matter of fact, your propensity to define people as enemies and act without mercy, while being gentle and kind to your friends.  The Chief Director is another person who is very similar.  Pairings you two together, you could have been great allies or great enemies, but there's not much middle ground.  It's a shame you have a powerful enemy, now.''



``I still don't see how we would have been friends.''



``I don't think you would have been.  But humiliating an enemy is a dangerous thing.  Doing it again would be terminal.  You'll need to be clever about your approach from here on out, so you aren't threatening them to the same degree.''



``I'm too tired to strategize any more, Glenn.''



``\emph{Think}.  What's motivating the Directors?  First thought that comes to your mind.''



``Fear.''



``Of?'' he asked, without a heartbeat of hesitation.



``Me?''



He shook his head.  ``More specific.  If they don't act now, what happens in the long run?''



``They can't control me.''



``People would recognize it, that the PRT didn't have the ability to control all of its heroes.  Some would act on it.  It would be devastating, damaging on a fundamental level.''



``Isn't that what you wanted?'' I asked.  ``Your `harbinger'?''



``It is.  Can you guess what I'm going to suggest, now?''



``You want me to make a move.  Powerful enough to shake them, break the status quo, not powerful or blatant enough to break my probation or give them an excuse to drop the book on me.''



``You'll be with the Wards by the week's end, if someone doesn't trip you up.  Do you think you can manage it?  A big success?''



``Maybe,'' I said.



``The moment you drop out of the public eye, you become vulnerable.  You've got a reprieve, but when you do act, you're going to need to act \emph{big}.  And you can't stop once that's happened.  Once you act, you'll be giving them an opening, and you have to keep moving after that.  Understand?''



``Yeah.''



``Keep the ramifications and the scale of your actions in mind at all times.  Use that strategic brain of yours.  Above all, be patient.''



\sectionbreak



``Now hearing case two-seven-two-four, Weaver.''



I stood.  ``I'm here.''



``For the matter of committee record, would you affirm that your full name and identity are a matter of public record, and that the committee is free to use it?''



``I will.''



``Will you state your name for the record?''



``Taylor Hebert.''



``Your date of birth?''



``June nineteenth, 1995.''



``You are a minor.''



``Yes.''



``Will you testify that you were not coerced into this arrangement?''



``I'm here of my own free will.''



``You were not offered any bribes or incentives that are not already a matter of record?''



``To the best of my knowledge, it's all been aboveboard.''



``As a minor, we ask that you have a guardian or respected professional to help guide you through the process, and to help verify what you're testifying.''



Before I could speak, I heard someone's chair scraping against the floor somewhere behind me.  Standing up.  ``Her father.''



I felt my heart leap.  I hadn't seen him when I'd peeked through the crowd behind me, but I hadn't been using my bugs either.  No use disturbing anyone.  I kept my eyes fixed in front of me.



``Would you please approach?''



I could hear him walk, but didn't turn to look.  Fuck, I was still hurt, still angry, even in the moment I was filled with relief.  He came to stand next to me, and my hand found his.  I squeezed, hard, and he squeezed back.



He was here \emph{now}, at least.  Not while I was in prison, not when I'd started my forays into the Wards.  But he was here now.



``Your name?''



``Danny Hebert.''



``State again for the committee record, your relation to her?''



``I'm her father.''



``You're aware of her standing in regards to the law?''



``I am.''



``And you've read the documents detailing her probationary status within the Wards?  Document two-seven-two-four-A?''



``I have.''



``You've read the statement and accompanying paperwork provided by Taylor Hebert, AKA `Weaver', document two-seven-two-four-B?''



``I have.''



``Do you hereby attest that all statements disclosed in the latter document are the truth, to the best of your knowledge?''



``Yes.''



I watched as the committee members paged through the documents in front of them.



My heart was pounding, and it wasn't just my dad's impromptu arrival.  This was it.  The moment my future hinged on.



I'd made enemies in the upper echelons of the PRT.  The question was whether they'd pull a maneuver, do something sneaky to undermine me or screw up the case to leave me stranded without anyplace to go but jail.



``I believe each of us have reviewed the files?'' the man at the center of the table finally spoke, looking to the others for confirmation.  ``Case two-seven-two-four has met the requirements for probationary admittance to the Wards.  She is to follow the stipulations as outlined in document two-seven-two-four-A.  Failure to comply will result in a return to medium security detention for a span of one and a half years or until such a time as she turns eighteen, whichever is longer.  Further, failing to meet the terms for probation will result in a forfeiture of any earnings or rights granted her by the PRT, which will be held in trust until such a time as she reaches the age of majority.  Do you understand these terms?''



``Yes,'' I answered.



``Yes,'' my dad said.



``With that, you are now a probationary member of the Wards, until such a time as you turn eighteen or violate the terms of your probationary membership.  Congratulations, Taylor Hebert.''



There were cheers from the sidelines.  Tecton and his group were among them.



``Next case,'' the committee members said.



My dad and I retreated into the aisle.  We made eye contact for what felt like the first time in an age.



``Thank you for coming.''



``I wasn't necessary.  You wouldn't be here if you didn't have someone else lined up.''



``It matters, dad.  More than you know.  Thank you.''



``Is this fixable?  Us?''



I frowned.



``What?'' he asked.  He opened the door so we could step out of the committee room and into the hallways of the PRT office.



``I've kind of come to hate that word.  `Fix','' I said.



``You don't think-``



``I don't,'' I interrupted him.  ``We can't fix `us', society can't be fixed.  It's impossible.''



He frowned.  ``I don't think it is.''



``Things \emph{change}.  Destroy them, rebuild them, you're just causing change.  Can't we\ldots isn't it okay if we \emph{don't} try to go back to the way things were?''



``You don't want to be a family?'' he asked.



``I \emph{do}.  But\ldots we tried to go back, after the city started to rebuild.  It didn't feel right.  It was \emph{nice}, but we were playing roles, and there was more stuff unsaid than said.  Lies, unasked questions.  Kind of unhappy at the root of it, you know?''



``I know.''



We found an empty bench and sat down.  I could see the Chicago Wards stepping out into the hallway, but they kept their distance.  Revel made her way out the door a few seconds later, and started talking to them as a group, at the opposite end of the hall.



``You're so far away,'' he said.  ``Doing things I can't even imagine, facing serious danger, even on a more mundane level, the way you're going to be living at the headquarters.  It's a fourteen hour drive.''



``Can't we visit, though?''  I asked.  ``Send emails every day, videochat?



``We can.  I'll come see you at the headquarters before I leave for home, see how you're getting by.  Maybe, if you need me to, I can pick up some essentials.  Things you wouldn't want to ask them for, or things they wouldn't know your preferences on.''



I wondered momentarily if my dad even know what my preferences were, nowadays.  I didn't voice those thoughts.  At the same time, I meant what I said as I told him, ``That sounds amazing.  Yes. Please.''



He smiled, but the expression faltered as he glanced a little to one side.  ``I think your team wants to talk to you.''



I nodded.  ``Talk to you in a bit?''



``Tomorrow,'' he said.



``Tomorrow,'' I replied, standing from the bench.  The Wards had turned to face me.



When I approached Revel and Tecton and the others, I cast a glance back.  My dad was still sitting on the bench.



It wasn't perfect, but it was a step forward.  It had to count for something.



\sectionbreak



``This space was for vehicles, but Stardust graduated three years ago, died a year after joining the Protectorate.  We've been using it for storing paperwork, and your moving in was a good excuse to get some things sorted out.  Your workshop.''



I nodded, doing my best to maintain eye contact.  Campanile was about eight feet tall.  I'd been given a complete physical and fitness test right off the bat, and I was five feet and nine inches tall.



The height difference put my eye level just a couple of feet above Campanile's hip level.  He wore a skintight suit, and there was little left to the imagination.  I thought I might have seen a ridge or a vein, in that split-second I'd glanced down to make sure my eyes weren't fooling me.



If I were more well adjusted, I would have been embarrassed, even offended.  Instead, I almost wanted to laugh.  Neither would have done well in terms of first impressions.



\emph{Focus on your bugs}, I told myself.  \emph{Look interested}.



``Talk to Tecton before you grab anything from the build room.  That's where we keep all the panels, portable walls and furniture for customizing our spaces.  Tools and everything would be down there too, but it's easiest to let Tecton keep it all in his workshop.  He's our only tinker, and it's not any harder to ask him for something than it is to go all the way to the basement.''



``Got it.''



``You're distributing this stuff to other groups, right?  The silk?''



``After I'm done outfitting my team, and you guys, our Protectorate.''



\emph{I'll give}\emph{Campanile}\emph{thicker fabric below the waist, maybe, }I thought.



``Well, there's a budget, so negotiate with Tecton on that front.  We all use the account, but the rest of us usually just dip into it to replace broken pads or lenses, stuff like that.  Tecton pays for materials, which is usually enough to empty the budget, but he makes and maintains knick-knacks and tools that he rents out to other groups.  Earns a bit of money to make up for taking an unfair share.''



``Got it.  I can do the same?  Selling the silk?''



``Yeah.  Might be easier, since your stuff can be mass-produced.''



I stared out at the workshop, glad for the excuse to look away.  Did he know how tightly the costume was clinging to him below the waist?



``It's good,'' I commented on the workshop.  \emph{Better than the one in my old lair.}



``Your bedroom isn't with the others at the hub, since there's not a lot of privacy there, and people are always coming and going.  It's more a place to kick back and nap if you've had a long patrol, keep some books and magazines, maybe some games.  You do have a nook, though.''



I nodded.  \emph{Maintain eye contact}.



``You're just down the hall.  Here.''



I checked out the bedroom.  It was better than my cell, but plain.  The fact that I could come and go when I pleased was a plus, even if I was confined to the building when I didn't have an escort.



``I can buy stuff to make it my own, right?''



``Yeah.  But you should know that they've got cleaners to do the PRT supplied laundry, sheets pillows, towels, the generic skintight suits.  You'll have to do your own laundry, and that includes any sheets you buy or whatever.''



``Got it,'' I said.  I very nearly glanced down to make sure the protrusion in his skintight outfit was still there, stopped myself.  Even in my peripheral vision, it stood out.  \emph{Seriously, that thing's as long as my forearm.}



``Computer's here.  PRT issue laptop.  Take some time, remove the crap.  If you don't know how, or if you're not sure what's dead weight on the system, ask Tecton.  Username is your codename, password to start with is your birthday.  Month-day-year, followed by your middle name.  Once you type that in, it'll set everything up automatically and prompt you for a new password.''



``Okay.''



``You've got a small bathroom just down here,'' he pointed down a short hallway, ``No shower, sorry.  There's one in the main area, not a lot of privacy, but you'll figure out the patrol schedules, and figure out when you can go shower without a chance of being bothered, if you're shy.''



\emph{Shy}.  I very nearly cracked a smile at that.  He was the one who should be bashful, but he just radiated confidence, instead.



``I'll manage.''



``Let's see\ldots there's the phone and earpiece, they'll get that to you soon.  Identification, the same.  Can you think of anything you need?''



``A few million Darwin's bark spiders,'' I said.  ``I could do with even just a hundred, but it'd mean a slow start.''



He didn't even flinch.  ``We can probably arrange it.''



``Black widows would work too.  Easier to find, but not nearly as good.  Maybe just need an escort so I can go out for walks.''



``We could arrange that.  I'm going out in an hour, meeting some kids at the hospital.  If you don't mind the detour, we could swing by a park or something.''



I tried not to imagine him in the pediatric's wing of a hospital.  \emph{You'd need to change.  Or wrap something around your waist.}



I didn't voice my thoughts.



``The hub is right down here, bottom of the stairs.  Command center, nook-slash-temporary bedrooms, spare costumes, televisions and everything else.''



Tecton, Wanton and Annex were at the bottom of the stairs.  Grace, Golem and Cuff were sitting at the computer bank against the one wall, but they were watching.  Grace had a wicked smile on her face.



I realized why.  The bastards.  They were pulling the same trick Campanile had, stuffing something in the front of their costumes.  Tecton, for his part, wore a mechanical suit, so he'd simply bulked out the crotch portion of his armor with additional armor plating.  Obvious, not even trying to hide what they were doing.  Wanton gave me a cheeky smile as I made eye contact with him.



For my part, I managed to keep my expression straight.



Over the course of seconds, Annex seemed to get more and more uncomfortable.  I made eye contact and maintained it as he squirmed.



``She's not reacting, and I'm feeling really, really dumb,'' he said.



``Aw, Annex, c'mon,'' Wanton groaned.  ``She would've cracked up.''



Grace was laughing, now.  Cuff, by contrast, wasn't moving her eyes from the computer screen.  \emph{She} was probably the ideal target for this kind of prank.



``Don't sue me for sexual harassment,'' Annex told me.



I smiled a little.  ``I'm not going to sue.  I've been around people who did worse.''



``It seemed funnier when we were talking about it before,'' Tecton said.  ``It's\ldots kind of awkward, right now.''



``It \emph{is} funny,'' I said, smiling, ``You guys \emph{did }get me, I was so busy trying not to stare at Campanile that I barely heard what he was saying about the tour.''



There were a few chuckles.



``I was thinking it was a bad idea,'' Golem said, ``With your background, that you might not like being picked on.  They gave me one, but I thought it was a bad idea to test you.''



``It was a terrible idea,'' Tecton said.  ``Juvenile.  But sometimes you need a cheap laugh.''



``They're embarrassing themselves worse than they're embarrassing me,'' I told Golem.  ``I'm okay with it.  I'm glad to have an initiation into the group.  Could have been far worse.''



``Alright guys, joke's over,'' Tecton said.  He unclasped and removed the metal codpiece from his armor.  ``She's right.  We're just embarrassing ourselves now.  Get rid of the damn things.  And I don't want to see them lying around anywhere.''



``I could keep it this way,'' Wanton joked.



``No you couldn't,'' Tecton said.  ``You'll forget about it, switch to your other form without absorbing it and wind up bashing someone unconscious with a foot-long silicon club.''



I glanced over my shoulder at Campanile, and saw him standing by the trashcan, no longer endowed.  He didn't look quite so ludicrous now.  Freakishly tall, yes.  Not freakishly \emph{long, }so to speak.



``Sorry,'' he said.



I shrugged.  ``I figure I've got blackmail material now.  Just need to get my hands on the security camera footage.''



He smiled and shook his head.  ``Welcome.  Be good.''



``I don't think these guys are setting the bar that high on the `good' scale,'' I told him.



He clapped one hand on my shoulder, then turned around to go up the stairs, leaving.



Annex had fled, but Wanton was taking his time in leaving, with Tecton giving him the occasional push to get him to walk faster.  Over by the computer bank, Grace and Golem were wrestling with something.



``Do it,'' I heard her.



``No way, no way,'' Golem responded



``Do it.  Just a little.''



She said something else I didn't make out.  It didn't go much further before Golem gave in.



Wanton doubled over mid-stride, falling to the ground.  Once he realized what had happened, he started thrashing in his effort to get the offending object out of his pants.  I had to avert my gaze before he inadvertently flashed me.



``Geez, guys,'' Tecton groaned, ``Too far.''



Golem rushed over, apologizing, while Wanton cursed at him, throwing the lump of plastic at his teammate.  Grace had fallen out of her chair laughing, and Cuff had done the opposite, putting her unburned arm on the desk and burying her face in the crook of it.



In the midst of the chaos, I made my way over to the computer bank and leaned over the keyboard, typing in the username and password I'd been given.  The desktop was up and running in heartbeats.  Access to nice computers was apparently a perk of being a hero.



I dug around for the files on the local powers, and began studying.  I \emph{tried}, anyways.  Grace's continued laughter was so infectious and unashamed I couldn't help but join in.



My new home, for better or worse.





