





``Sorry\ldots I'm\ldots so\ldots''



He didn't finish the sentence.



I could sense him slowing, using the bugs I'd planted on his costume.  I stopped and waited for him.



``It's fine, Theo.  You're doing me a favor.''



``Doesn't feel like it,'' he said.  He bent down, hands on his knees.



I waited for him to get his breath.



``I might throw up,'' he added.



I backed away a step.  ``Just getting the chance to run, it's cool.  Not many others are willing to meet me at seven to run, much less six weeks in a row.  Grace is athletic, but she got sick of it fast.''



He mumbled something I couldn't make out.



``What?''



``I'm not athletic.''



``You're getting better.  We just got a whole two blocks.  That's not bad.  About as good as I was when I started.''



``Not fair to you, make you suffer for how much I suck.''



``It's fine.  It's \emph{nice }to get outside.  Kind of a pain to have to get someone to come with if I want to go outside for no particular reason.  If I don't get the exercise here, I can use the treadmill back at the headquarters.  Don't feel obligated, if you're not enjoying this.''



``I don't.  I'm\ldots it's good.  I want to get fit.''



``Well, in that case, don't worry about it.  We're both benefitting,'' I said.



He made it another few steps before he was hunched over again, still breathing hard.



I felt a pang of sympathy, suppressing a smile at the same time.  ``Come on.  We'll walk one block, then try running another, walk the rest of the way.''



He was still panting for breath as he obliged.



I found myself missing Brockton Bay.  It wasn't the most beautiful city, or the most active.  Or the most \emph{anything}.  There were already things going on around the portal, but it wasn't a city with a lot going for it, and it hadn't been even before the intense series of events had laid waste to the shoreline, set a water-filled crater in the northwest corner of the downtown area and left an entire swathe of the city so fucked up with random, horrifically dangerous effects that it had to be walled off.



Maybe I wouldn't have felt the same way if I hadn't grown up there, but I liked the balance in Brockton Bay.  The way there was everything I could want, as far as malls, shopping centers, theaters.  It was a big enough city.  Yet there was just as much room to wake up early in the day, when others weren't out, and have Brockton Bay to myself.



Chicago wasn't like that.  It was busy, and it was busy in a way that got in my way.  People were already up if I got up at six in the morning to go run.  Some were still up from the \emph{previous} night, having spent the entire evening at clubs or whatever else.  Everything was taken to an extreme, it seemed, in drama, opinions and ideas.  It made it a little harder to sympathize with Chicago's equivalents to the people I'd been helping in Brockton Bay.  A little harder to sympathize with \emph{anyone}, really.



I was feeling cramped.  I wasn't a social person at my core, and being here, like this, never allowed to be out and on my own, it rankled.  I liked time on my own, with the internet or a good book, even a \emph{bad} book, to get my mind settled down, my thoughts in order.  It wasn't that I didn't like people, that I didn't like \emph{company}, but too much was too much, and I had no elbow room here.



Whether they knew it or not, the PRT directors had found a fitting way to punish me.  Hopefully it wouldn't go any further than this.  I'd done as they asked, I was staying under the radar, and though I didn't plan to \emph{stay} there, I didn't think they had any reason to make my life more difficult.  I had my suspicions that my phone and computer were tapped, so I was careful about what I browsed and how I communicated.



With luck, they would forget about me until I was active again.  With \emph{more} luck, I wouldn't have to worry about them much longer.  The Director from Toronto, the guy I hadn't been able to place, had already quit.  Wilkins and West were still active, but the woman at the end of the table was under scrutiny.



There was stuff going on behind the scenes, and speculation was rampant on the Parahumans Online site.  Satyrical's name had come up.  As far as  could tell, the Vegas capes had gone rogue, and they were apparently targeting the more corrupt elements of the PRT.



I wasn't a hundred percent sure how to feel about that, but I wasn't complaining if someone was taking down my enemies for me, especially if it was in a more or less safe, legitimate way.



``Hey,'' Theo said.



I turned to look at him.



``When you were dealing with the Slaughterhouse Nine back in Brockton Bay, you fought Jack Slash, right?''



``Yeah.  Kind of.''



``Kind of?''



``He doesn't really \emph{fight}, unless he's got his people around him and the fight's unfair.  Mostly, I was chasing him around, trying not to get killed in the process.''



He frowned.



``Worried?'' I asked.  ``You'll have help.''



``So will he,'' Theo pointed out.



``True.''



``I'm\ldots I'm not good at this.  Everything Kaiser was, I'm not.''



``That's not a bad thing.  He was an asshole.  You aren't.''



Theo managed a weak smile.  It was hard to identify just how he would react in regards to things.  Backed against a wall, faced with a serious threat, he showed courage.  I'd seen him on patrol, and for all his worries, he did follow through.  He had against Behemoth, in what was almost his first time out in costume.  Talking about his family, though, I couldn't pin down just what he'd say or do.



The feeble smile, was that genuine?  Had I hurt him, left him in a position where he wanted to defend his family but couldn't because of what they were?



``I don't fit the typical cape mold,'' Theo said.



I resisted the urge to tell him I didn't either, but I didn't.  I remembered a tidbit of advice I'd heard Tecton giving, and listened instead.  ``You're feeling nervous.  Anyone would.''



``The running, I don't feel the difference,'' he said.



``Slow gains, but they're there.''



``The \emph{training} helps,'' he said.  ``The training feels concrete, like I'm getting significantly better.''



``You want to train when we get back?''



``I don't have long before I have to patrol.  A short one?''



``Sure.  Come on.  Run one more block, throw up if you have to, then we walk back.''



He made a sound partway between a gurgle and a groan, but he followed me as I took off.



Running at first, then walking, we took a different route coming back than we'd taken on our way out.  The trees by the lake were aflame with autumnal colors, and I could see a handful of college students and older folk gathered, enjoying the serenity of the lake, the perfect temperature.  Tranquil.



That was something I could get behind.  I would have loved to sit by the lake, given the opportunity.  The trouble was, I never got the chance.  I was leashed to other people's schedules, my excursions had to be in another person's company, and nobody had really seemed keen on the idea of going out solely to go and sit at the lakeside.



As penance went, it was pretty light, but the overall effect of this restriction was wearing on me in a way that the jail cell hadn't.



We reached the PRT headquarters, one of two in Chicago. It was squat, broad, and not terribly pretty, but it sported a statue on the roof that had been paid for by an old member, Stardust.



Once inside, we made our way up to the top floor, where the Wards' rooms and the `hub', as the others called it.  It was a label that made me think of prison, and that, in turn, pushed me to think of it more as a common area or a lounge.



``Gym?'' I asked.



``Yeah,'' Theo said.  ``Let me get my stuff on.  I'll meet you there.''



I tapped into the supply of bugs that were stored in my workshop, withdrawing an assortment of flies, beetles and cockroaches, depositing the ones that I'd collected during the `run'.  It wasn't many, but I didn't need much.  Enough or three or four swarm clones.



I stopped by the kitchen to collect some silverware, then made my way down one floor to where the gym was.



Golem arrived a minute after I got there, decked out in his costume.  It had changed from its first iteration, complete with a layer of spider silk and heavy armor over top of it.  He wore a mask with a neutral, almost solemn face, and fan-like decorations at his waist and shoulders, the spaces stretching between the slats painted white, a darker metal composing the frame and edges.



The image consultant was having fits, no doubt, but the first and most important goal was for Golem to be effective.  We were getting there.  Image would come later.



``Hey,'' Kirk greeted us, stepping out as Golem arrived.  He wore a t-shirt and yoga pants, and was glistening with sweat.  His head was shaved, and his skin was a striking jet black.  ``You guys sparring?''



``Training,'' I said.  ``Not sparring, really.''



``Can I watch?''



I looked at Golem, ``Are you okay with it?.''



``I'm the one embarrassing myself, you mean.''



``I think you're past the point where you're embarrassing yourself,'' I said.



``You can watch if you want, Annex.  Wouldn't mind helping clean up,'' Golem said. ``I can't promise it'll be anything special.''



``Not a prob,'' Kirk responded.  ``Kind of curious to see where you're at.''



We made our way inside.



The area was divided, with workout machines taking up one half, and an open area for sparring and dance and whatever else on the other half.  Floor panels, varying in the depth and degree of padding offered, were neatly stacked in one corner.



We moved to the open area, but we didn't set up any padding for the floor.  My bugs flowed through vents and from the hallway outside, and they filled the room, covering every surface.



The bugs congealed into a human figure, and Golem took action.  His fingertips ran along the white `fans' at his waist, then he jabbed one hand inside.  A hand of concrete lunged out of the floor to dissipate the swarm.



A little slow, but not bad.



Another part of the swarm congealed into a rough decoy, and Golem clutched it in a fist of concrete.  Faster this time.  The bugs seeped out through the gaps in the fingers as the hand retreated into the floor's surface.



Each panel of the fan was a different material.  Concrete, steel, granite, wood.  Common materials were in easy reach.  Less common ones were a gesture away.  Two at once, this time.  Two figures to strike.  Golem caught one with his right hand, but I moved the other as he reached for it with his left.  He wasn't quick enough to catch it, and the angle was poor.



I drew a butter knife from the pocket of my shorts, raised it above my head.



Golem was watching for it.  He dug his fingertips into the topside of one panel, his thumb into the underside.  Identical digits sprouted from the knife, forming half of a fist that had closed around the edge.  The knife became a club, one with no cutting edge.



I threw the weapon aside and turned my attention towards creating more decoys.



I feinted, now, misleading him about where my clones were moving.  He struggled but managed to deliver the hits.  Dragonflies and faster insects formed a more mobile body, and I avoided the strikes, right up until he started creating hands that sprouted forth from limbs that were already sticking out of the ground: branching barriers to limit movement.  I tried to simulate the general effect of the obstacles, and Golem took the opportunity to deliver a finishing blow, crushing another swarm-decoy..



``Hit them harder now,'' I said.  Running\emph{, }I tried to raise expectations for myself.  Here, I did much the same for Golem.



The movements became more violent.  A hand cupped around one swarm and then pulled it against the ground, melding back into the surface.  Bugs were squished against the spacial distortion field, and my swarm's numbers were severely reduced.



Another was squashed against the wall, but the surfaces were different materials, and the hand couldn't simply sink back in.  This time, there was an audible thud, eliciting a heavy rattling from the exercise machines on the other side of the gym.



I drew my swarm together into a rough shape, not a person, but something larger, a touch bigger than Crawler, smaller than Echidna, bipedal.



He hit it, and I reformed it.



``Hit it harder,'' I said.



He hit it again, drawing two hands together as if he were squeezing it.  There was no substance to the monster's body, though.  I judged that he wasn't doing enough damage and simply reformed it.  The monster advanced on him.



I stepped a little closer, raising my voice.  ``Come on, Theo!  Hit harder!''



Golem dropped a foot as one leg slipped into the concrete floor.  A facsimile of his boot rose out of the floor, complete with cleats.  The speed and force of it would have been enough to lift one of Rachel's dogs, so I obliged by moving the `body' of the swarm monster, raising it.



As the foot continued to rise, Golem's leg disappearing up to the knee in the floor, he pushed one hand into the fan, causing a limb to drop from the ceiling right above the rising spiked platform that was Golem's boot.  My creation was sandwiched between the two, and the collision had enough of an impact to make Kirk and I stumble.  I had to turn my head to keep the dust from getting in my eyes.



``Is that-'' Golem started.



Before he finished the sentence, I had a second butter knife drawn, the tip pressed to his throat.



``Keep your eye on the threats,'' I said.



``Not very fair,'' Kirk commented.  ``Playing dirty.''



``No,'' Golem said.  His voice wavered, which was odd, considering I wasn't doing anything that was actually \emph{threatening}.  Something else had shaken him.  Had he taken the lesson to heart?  ``I's good.  That's the kind of lesson I need to know.  It's why I'm training.''



``Jack's going to throw some scary motherfuckers at you,'' I said.  ``But he'll be looking for an opening.  Always, always watch your back.  Don't forget to watch your friend's backs too.  You probably won't die if you do, but you might wish you were dead, when you see what Jack and his gang do to them.''



Golem withdrew his arm from the panel, but his leg was harder to free from the ground.  By the time he was standing straight, the leg that stuck out of the floor had become more or less permanent.  In another area, fingertips stuck out of the floor.  There were also the branching `trees' of hands that had formed barriers.  Without us even asking, Kirk stepped forward, his body liquefying as he flowed into the surface, smoothing it all out as though we'd never been there.



When he was done, he emerged to survey his work.



``Thank you,'' I said.



``Interesting to watch.  Figuring out ways to apply his power?''



``Pretty much.  Tricks for his repertoire, building some familiarity with using his abilities, attacking to recognize threats and attack without hesitation when needed.''



``You really buy that Jack's going to wake up from some cryogenic sleep just to fight some kid who didn't even have powers when they last met?''



``Yeah,'' I said.  ``Believe it or not, with what I know of Jack, it makes perfect sense.''



``Huh.''



``You're on board, right?'' I asked.  ``With the plan?''



Kirk nodded.  ``Seems a little crazy, but doesn't hurt, given the stakes.''



``End of the world,'' Golem said.



``End of the world,'' I agreed.  ``We'll get as many on board as we can.  Either we avert it, or we soften the blow.''



``Assuming we can figure out what it is,'' Golem said.



``Yeah,'' I said. ``You said you had patrol soon?''



``Eight twenty.  Then school after that.  I'll see you this afternoon?''



``Yeah,'' I answered.  I made my way to the common area and took the first unoccupied spot at the computer.  Grace was there, but she wore a school uniform, and had homework spread around her.



``Don't say a word,'' she told me, clearly annoyed.



``Wasn't going to,'' I responded.



I logged in, and was greeted by the customized desktop.



C/D: Endbringer
-3:21:45:90



C/D: End of World
593:19:27:50



The first counted upward, the other counted down.



Three days had passed since the estimated arrival of either the Simurgh or Leviathan.  Behemoth had been early, but whatever factor pushed that to occur wasn't at play here.



It made sense that they wouldn't maintain the schedule they had been.  Since the Simurgh had arrived, roughly three and a half months had passed between each attack.
These coming days and weeks would speak volumes.  Were the Endbringers going to alter their tactics?  Would the schedule continue at its accelerated pace, with Behemoth appearing in seven to ten months?



Something else altogether?



My eyes fell on the second clock.  The countdown.



593:19:25:23



\blacksquare



``No joke?'' I asked, the second the elevator doors were open.  Cuff was waiting on the other side.



``She's here,'' Cuff said.  ``Not \emph{here}, here, but she's showed up.''



I was in full costume, my flight pack on, an insulated box for my bugs tucked under one arm. my phone in hand.  I was chilled to the core of my body, my lenses fogging up from the adjustment from outdoor temperature to indoor temperature.



I didn't need to ask who.  I knew well enough.  It was a question that had been lurking on everyone's minds.  \emph{Which one, where}?



I pulled off my mask as I followed her to the common area, and reached out to accept the glasses my bugs were already fetching to me, putting them on.  The same images played on each of the screens.



The Simurgh, her silhouette barely visible in the midst of the clouds.



``What city?'' I asked.



``Not a city,'' Tecton said.



Sure enough, the camera angle changed.  Water.  Coastal?



No.  Too much water.



Ocean.  She was attacking the ocean?



It clicked when I saw the text at the bottom of the screen for one news report.  \emph{BA178 under siege}.



Of all of the sensitive locations in the world, the Simurgh had chosen a passenger airplane.



``Are we-'' I started to ask.



``Can't,'' Tecton said.  ``No solid ground, and none of us fly.''



``I fly,'' I said, but I could already guess the follow-up answer.



``Vehicles and tinker equipment aren't going to cut it.  Too easy for her to interfere with,'' Tecton said.



``Order came down from the top.  Natural fliers only,'' Wanton added.



``We're too late to join in anyways,'' Grace said.  ``I can't imagine this'll be a long, drawn-out, knock down fight.  We got almost no warning.  It's like she dropped straight down from where she was and picked a fight with the closest target.''



I thought of Armstrong's insistence that we capitalize on our victory, mass in numbers to allow for another decisive victory, instead of showing up in smaller groups, with inevitable attrition.



All this waiting, all of the restlessness, watching the countdown clock tick well beyond the estimated date, and we couldn't even fight.  I wasn't sure how to feel about that.



I watched on the screen as Legend, Alexandria and Eidolon engaged the Simurgh.  She avoided the worst of their attacks, primarily through the only cover available – the airplane.



Half of the screens were showing the same video footage, though they were different channels, different organizations.  The other half were showing information.  The flight route, the people in the plane.



If anything here was special, the only one who knew would be the Simurgh.



My teammates didn't talk much as we watched the fight progress.  In one instant, it seemed, the dynamic changed.  The heroes began trying to attack the plane, and the Simurgh started trying to defend it.



For eleven minutes, she managed, using her telekinesis to move the craft, her wings and body to block it from being damaged.



A fire started on the body of the ship as Eidolon tore into the Simurgh with a reality warping power of some kind, complete with lightning, fire, distorted light, and ice.  The Simurgh cast the craft aside in the following instant, letting it flip, burn and tumble before hitting the water and virtually disintegrating.



That done, the Simurgh ascended, rising into the clouds.  A few capes tried to follow, but Scion wasn't among them.



``How long was the fight?'' I asked.



``Not long enough for Scion to show,'' was all Wanton said.



``Forty minutes?'' Tecton asked.  ``About forty minutes.''



I'd spent more than half that time hurrying back to headquarters, hoping I wasn't missing my ride.  Now this.  It was a farce.



``Now we wait,'' Grace said, ``And if we're lucky, we find out what she just did.''



That was it.



It was almost a letdown, more than a relief.  I couldn't say she'd been softballing us, because it was the \emph{Simurgh}.  For all I knew, this was the most devastating attack yet.  We wouldn't know until later on.



Virtually no casualties, the planeload of people excepted.  Nobody was reporting anything about heroes dying, but it had been clear enough from the footage that this hadn't been a serious loss.  Barely forty capes had been out there, and I hadn't seen any die.



Yet I felt irrationally \emph{upset}, if anything.



I turned and walked away.  I let the strap of the incubation box slip from my shoulder to the crook of my elbow, caught it with my hand, and then transferred it over to the arms of my flight pack.  It meant I didn't have to stop or bend down to set the incubation box at the base of the stairs.  I didn't go up to my room or my workshop, though.  I made my way \emph{downstairs}, instead.



I was grateful to see that Mrs. Yamada hadn't left yet.  Her things were packed, but she'd settled into the office, and was reading a small book.  A television was on in the corner, muted, showing what was happening with the Simurgh.



``Taylor.''



``Do you have a minute?''



``Of course.''



She stood and crossed the room to close the door.  I hadn't realized I'd left it open.



``It was about the best we could hope for, going by what we know now,'' I said, ``And I feel worse about it than I did about New Delhi.''



``You've been preparing for this, anticipating it, for some time.  Mentally, you were preparing yourself for more losses, steeling yourself.  That takes a lot out of you, and you were robbed of a chance to do something.''



My phone buzzed.  I glanced at the screen.  My dad.  I sent him a message letting him know I was fine.



``Sorry,'' I said, putting the phone away.  ``It was my dad.''



``Don't be sorry.  It's a good sign if you're reaching out to your dad, or vice-versa.''



``It's bad manners,'' I said.  ``But okay.  Back to what we were saying before.  I'm almost feeling\ldots disarmed?''



``Disarmed.  Good word.''



``I've been sort of enjoying the peace, the fact that the Protectorate are dealing with the meanest bastards around, the Folk, the Royals, the Condemned.  But I was telling myself it came down to the Endbringer fight.  That I'd participate, I'd wake up, \emph{fight}.''



``Isn't it better if you don't have to?''



``No,'' I said.  I stared down at my gloved hands.  ``No.  Not at all.''



``You came from a bad place, and, like we've talked about, you reinvented yourself.  Maybe a lot of your identity is rooted in your concept of yourself as a warrior.''



``Maybe,'' I said.  ``But whether it's true or not, it doesn't change how I feel.''



``I expect a lot of people around the world feel the same way.  It's very possible she calculated things to achieve this effect.''



I nodded.



``What do you think would be a best case scenario, Taylor?  If everything went the way you were hoping it would, deep down inside, what would happen?''



``New Delhi would happen,'' I said.  Except without the severe losses.  We'd lose people, some place would get damaged, but we'd kill another Endbringer.''



``Is that realistic, do you think?''



``No,'' I said.  ``I \emph{know} it isn't realistic.  We went decades without killing one, and it's stupid to imagine we could kill two in a row.''



``What's a more reasonable expectation?''



``That she'd show up, and we'd fight, and we'd drive her off without too many casualties.''



``In either of these scenarios, do you envision yourself playing a role?  Maybe as big a role as you played in New Delhi?''



``I'm\ldots Sort of?''



She didn't seize on anything there, nor did she ask a follow-up question.  I took the opportunity to reflect on it.



``Yeah,'' I eventually said.  ``Maybe not as big a role.  Again, that's unrealistic.  But I want to \emph{help}.''



``If the Simurgh wanted to deliver a hit to morale, this would be a way to do it,'' Mrs. Yamada said.  ``After New Delhi, a lot of capes were hoping to make a difference, to be heroes.  Her choice of venue, the short battle, the narrow focus, it denied everyone the chance.  Not just you.''



``I need to be stronger,'' I said.  ``I'm supposed to be one of the people that's around for this prophesied end of the world.  Except I'm not getting chances here.''



``Can you talk to your superiors?  To Revel?''



``I've hinted at it, that I could stand to sidekick around on patrols.  Nobody's taken the deal.  Not with me.  They took \emph{Golem}, but the adult capes like him, because he's polite to a fault, works his ass off, and his power is good.  \emph{I'm} good, but I wind up being a partner more than a sidekick.''



``You've been training with Golem.''



``Yeah.''



``You're due some of the credit for his forward strides, I'm sure.''



``I'm not-'' I started, then I made myself stop.  Too much emotion in my voice.  Calmer, I said, ``I'm not looking for reassurance, or for compliments.  I'm just\ldots''



I struggled for a way to end the sentence.



``Let's use the `I feel because' line.  Frame your emotions better.''



I drew in a deep breath, then sighed.  ``I feel spooked, because \emph{something's} coming and it's going to be ugly, and I'm not prepared.  I feel less prepared with every day where nothing happens.''



``I imagine your teammates feel spooked too.  You've mentioned what they're going through.  Golem is likely going to be baited out by Jack Slash at some point in the future.  Cuff has limited dexterity with her right hand, to the point that she's having to relearn to write and type.  I'm not discussing anything confidential, to be clear; only what you've mentioned to me in our previous sessions.''



I nodded.



``Golem has your support, I know.  They all do, in some respect.  In terms of what Cuff is going through, I know your team is dividing the workload in helping her with paperwork.  That says a lot.''



``Supporting each other.''



``It sounds trite, but I think there's a truth in it.  You have legitimate fears about what comes down the road.  But keep in mind that you're not alone in this.  Maybe you've hit a ceiling for the time being, in your own growth and development.  But you can still \emph{progress}, if you're helping your teammates, assisting them in conquering their demons and improving their abilities.''



``Yeah,'' I said.  ``It doesn't feel like enough.''



``It may not be, but it's \emph{constructive}.  Perhaps you'll feel less disarmed if you focus on the tools and, so to speak, the weapons at your disposal.''



``Maybe,'' I answered her.  ``But I hate feeling helpless.''



``Part of the reason you feel that way is because you're waiting for opportunities to come to you.  You waited for the Endbringer, so you could flex your talents in unimaginably high stress environments.  It's good, I think, that you waited, that you had a moment to breathe.  I think you should strive to retain that peace, because it may help you enter a better headspace.''



It was similar advice to the parting words Glenn had left me with, but they opposed on one front.  Mrs. Yamada would have been happier in general if I maintained this indefinitely.  Glenn would be wanting to see me \emph{acting}.



It was time to act, whatever Mrs. Yamada said.



``Thank you,'' I said.



``You feel a little better?''



``Not really,'' I admitted.  ``I'm not even sure I understand all my feelings.  But I feel like I've got more of a plan, now.  I appreciate it.''



``It's what I'm here for.  Or at least, I'm here for one more hour, and then I fly back to Boston.  I'll be around next Friday, after I finish another circuit.''



``Cool,'' I said.  ``I'm glad you were here today.''



``I am too,'' she answered.



When I stood from my chair, she did too.  She stepped forward and gave me a hug.



I wasn't sure how normal that was, but I'd remarked once on how few hugs I got, and how some hugs I'd given or received in the past had been meaningful moments for me, and she'd asked if I wanted one from \emph{her}.



Somewhere along the line, t had become something of a habit, as we ended our sessions.  I gave her a little smile as we parted.



I made my way back to the common area, and seated myself at the computer.  The others were still following what was happening on the larger monitors.  The defending heroes had frozen the plane's half-submerged wreckage and they were preparing quarantine measures.



Whatever the reason for this particular attack, I doubted it would be clear anytime soon.



Instead, I seated myself at the computer, and logged myself in.  The timers ticked away.



Once I'd updated the timer for the recent attack, it read:



C/D: Endbringer
149:22:59:59



C/D: End of World
579:07:14:53



Inching down steadily.



Mrs. Yamada had been right, I mused, as I found the files on the local kingpins and warlords.  I was doing myself a disservice by waiting for opportunity to come to me.  If I was going to do as Glenn had suggested, and make a calculated play, I needed to \emph{act}, rather than hope for another chance like we'd had in New Delhi.



Looking at the others, I wondered if it was best to manipulate them or get them on board.  Manipulation was almost \emph{kinder}, because it absolved them of guilt.  Simply making sure we were in the right place at the right time, luring a local power into a fight, with  a plan already in mind\ldots



No.



Chevalier's Protectorate, ups and downs aside, was more about honesty.  I wanted to tap into Skitter's strengths, her ruthlessness, but I also wanted to be a hero.  \emph{That} was at the core of what I had achieved in New Delhi.



``Tecton,'' I called out, as my eyes fell on a portrait of a supervillain with a mask of an upside-down face.  An established power, located at the city's edge for nearly ten years.



\emph{Too established?  }I didn't want to set another ABB fiasco in motion.  There were advantages to being open.  The ability to ask questions, get feedback.



``What is it?'' he asked.



``There's something I want to talk to you about.''





