





Wind stirred the snow that had piled up at the rooftop's edge.  As it entered the space over the Chicago street, city lights caught the flurry and made it almost luminescent, whirling clouds in intense, intricate patterns.



I was, in other words, bored beyond comprehension.



Stakeouts?  Not nearly as interesting as they were in the movies.  Not even as interesting as they were in the TV shows where nothing happened and the cops complained about how dull things were.



No, this was a \emph{special }kind of boring, where I was told to limit how much I \emph{moved}, because of the half-a-percent chance that the targets in the building on the other side of the street might look out a window, and the ensuing one-in-a-thousand chance that they might actually be able to \emph{see} me perched on the rooftop, surrounded by snow in my dark gray and white costume.



A boring, even, where I wasn't allowed to read or listen to music.



``\emph{Weaver},'' the voice came through my earbud.



``Talk to me.  Please.''



Grace complied.  ``\emph{Police chief and the Mayor are talking to Revel and the Director.  Thought you'd want an update}.''



``You could give me minute by minute updates on \emph{golf} and I'd love you forever.''



``\emph{Hyperbole.  That's not like you.}''



``It's been a while,'' I muttered.  I shifted position to bring my feet up onto my `bug box'.  The case was insulated, but there was \emph{some} heat loss, so it included a heater that turned on periodically to maintain a consistent internal temperature.  At the same time, I was wearing a PRT issue winter-weather costume beneath a doublethick silk `Weaver' costume, complete with a hood, shawl and something of a skirt.  It took time for my fingers and toes to get cold, so things more or less evened out with the heater.



``\emph{Well, this is your five minute check-in.  Again.}''  I could hear the noise of a show or something on in the background.



``Thank you, Grace.  Situation unchanged.  Target's grabbing a late dinner.  There's seven others working under him.  Nothing special in their chatter.  There's plainclothes capes in there, but they're not using names.''



``\emph{You're sure they're capes}?''



``He warned them when they stepped inside that he'd act the \emph{second} they used powers, so\ldots yeah.''



``\emph{Gotcha.  I'll be in touch in another five min}.''



``These five minute check-ins make it so much worse,'' I groused.  ``It's like, if it weren't for those, I could let time slip by, but no.  I get measured reminders of how long I've been here.''



``\emph{This was your idea}.''



``Dumb idea,'' I commented.



``\emph{You were the one who wanted to do the stakeout, even},'' she reminded me.



``Kind of thought I'd get to read,'' I said.



That, and it had been a way to \emph{finally} get some time to myself.  We had run it by the Director, and I'd known right off the bat that he was \emph{itching} to shut me down.  Orders from above, no doubt.  A way to get credit with the guys upstairs.



Still, I'd explained how my bugs would let me track the target's movements.  Our boss had okayed the job, with certain restrictions.  The surveillance had to be airtight, with the check-ins, a mandate that any breaks had to fall between check-ins, and the restrictions on entertaining myself or drawing attention.  At the same time, he'd said with a smile, the PRT rulebook said a Ward couldn't be forced to undertake or carry out a mission.  If I wanted to walk away, I could.  If I got too cold I \emph{had} to.



He wanted me to quit.  To exercise a measure of control over me, so he'd have something to leverage against me at a later date.



Six hours in, I'd left for three bathroom breaks, each between four and a half and five minutes in duration, and had relocated three times, as our target went out to lunch and then returned to check on the business.  Wanton and Annex had both come to keep me company, until the Director had found something else for them to do.



Then Revel had come on shift, and I had an ally who wasn't just ready to go to bat for me, but \emph{able}\emph{to}.  She was working reduced hours after her head injury, deferring more tasks to Shuffle, but she was still the boss.  She'd read the logs from the check-ins, called me to verify facts on the drugs and guns I'd noted moving through the apartment, and then reached out to the Director.



That had been two hours ago.  Somewhere in the midst of her battle with the Director, she'd reached out to the police chief and mayor.  She would be trying to sell them on our plan.



Or, it was easily possible, they were sold and they were trying to get the ducks in a row and favors pulled to make our plan a reality.



And with all the excitement that was no doubt happening over there, I was sitting here, a little cold, wishing I'd saved a little something from the lunch I'd packed into my plastic Alexandria lunchbox.



The lunchbox was a memento, really, an impulse I'd justified in the moment by telling me it fit with my general camouflage, that it was ironic.  I hadn't counted on how long I'd be left to stare at it, while my bugs tracked the target going about his day.  It made for a long time spent ruminating on past events, debating just how the bureaucrats could sabotage me, intentionally or otherwise.



For several dangerous minutes, I'd seriously considered going back to the Undersiders if this mission got derailed.  I'd stopped myself before I got too far into that line of thinking, knowing it was a trap that would lead to me compromising, giving up in a way.  Playing into the Directors' hands.



No, I wouldn't go back.  I missed them; scarcely an hour went by where I didn't wonder how they were getting by, but I wasn't allowed to contact them.  I wanted to know how Imp had changed in response to Regent's passing, if Grue was getting enough support, or if Rachel was managing in the cold on the other side of the Brockton Bay portal.  Was Tattletale using her power too much, still?  How was Sierra managing as a corporate magnate and front-man for a villainous organization?



Hell, how was the Boardwalk getting on?



They were questions I couldn't ask or answer without raising red flags with the people who were watching me for the slightest excuse.  I'd cheated and sent letters, written by my bugs, delivered to a mail box while I was hundreds of feet away, and I'd received `fan letters' with coded messages from Tattletale.  It wasn't enough, didn't have the details I craved.



``\emph{Five minute check-in},'' Grace said, interrupting my train of thought.



``Situation unchanged,'' I replied.



``\emph{Stuff's happening over here.  Revel is right beside me.  She'll fill you in.}''



I perked up a little at that.



``\emph{Weaver.  Revel here.  I've talked it over with everyone that matters and too many people that don't, and they're saying it's okay.  Tecton and the rest of the Wards, minus Grace and Wanton, will be mobilizing shortly.''}



\emph{``}We're good to go?''



``\emph{Shortly.  PRT trucks are already en route and will be standing by, when they're not actively transporting your teammates.  Campanile, Brazier, Shuffle and Gauss will be a short distance away, but they won't engage unless this goes belly-up.  This is your show.  You and the Wards.  Quite a few people hoping you guys can pull this off.  A handful hoping you fail.''}



Like the Directors.  ``Got it.  Do me a favor and fill me in on everyone else's status and locations until they're within a twelve-hundred feet of me.  Coordination is going to be key here.''



``\emph{Grace will handle it.}''



Not a hundred percent necessary, but it would keep me sane.  I suspected the remaining minutes of waiting would be as bad as the first three hours had been.



``\emph{We're controlling traffic},'' Grace said.  I could hear others speaking in the background.  ``\emph{Flow through the area should slow and eventually stop.}''



``Good to know,'' I said.  My eyes roved over the face of the building opposite me, while my bugs tracked our quarry.



``\emph{Where do you want your team}?''  Revel asked.



\emph{My} team?



``Keep them in the vehicles,'' I answered.  ``I'll let them know where to set up when things are underway.''



I stood up from my perch, making sure that our target and his employees weren't watching out the windows before I stretched.  I was alternately cool and toasty warm, where different body parts had been closer to the vent, and my costume layers thicker.  Not \emph{cold}, though.  Not so much that I'd be affected.



Snow slid off the top of my hood as I bent down, lifting the insulated box with my bugs inside and setting it on the roof's edge.  It was essentially a thermos, but as lightweight as the materials were in the case and the heating system, the bugs I'd packed inside made it heavy.



I worried it would be an issue in my plan.  With roughly eight hours by myself to think, I'd considered various ways this could go.  Tactics our enemies could employ, things that could trip us up, ways our supervisors could derail the plan, but this forty pound box was something that rested entirely on my shoulders.



``\emph{We're close to the perimeter},'' Tecton reported, his voice buzzing in my ear.



I pressed a finger to my earbud, ``I'm going to get us started.  Sound off from all corners, please.''



``\emph{Roger from HQ},'' Grace said.



``Roger-roger from the field team,'' Tecton said.  ``Just reached perimeter.  Sending Annex and Cuff your way.  Golem and I will be working.''



I stepped over to the rooftop's edge.  The streets had gone quiet.  The unsteady evening traffic that had a way of continuing in the dead of night had stopped, leaving the area more or less isolated.   I'd spent the better part of the day organizing bugs in the surrounding buildings, and I now moved them into position.  Swarms formed into large `x' marks on major exits, elevators and stairwells.  In higher traffic spots where people were more likely to move, I drew out words with the swarm.



`Cape fight in progress.'



I suspected this was a not-insignificant part of how Revel had managed to get the police chief and mayor on board with the plan, despite any protests or manipulations from the Director.  The chance of bystanders getting caught up in this was minimal.  As minimal as it was possible to get in the midst of a larger city, anyways.



I activated my flight pack and crossed the street, simultaneously making my way down to the ground.  Not so hard, with the extra weight that made up my burden.



The doorway that led into the lobby of the apartment building required a keycard or a number punched into a resident's phone upstairs.  Not so difficult, after a day's surveillance.  My bugs were already prepared to knock a phone off the hook in an older woman's apartment, a moment after I'd found her name on the board and dialed the number.  Much as I'd done in Tagg's office, I had my bugs punch the buttons.



The door buzzed.  I walked backwards into it, carrying the insulated box, then dropped the box in the base of the lobby, opening the little door.



The bugs flowed out of the box and disappeared into the air vents.  Slowly, they made their way up to the apartment of a local supervillain.  A black market storehouse first, an apartment second, really.  The only reason it seemed he slept here was convenience.  The old adage of not shitting where one ate fell apart when ninety percent of the day was spent eating.



I knew how easy it was to fall into that trap.  I thought of the Boardwalk and felt a trace of nostalgia.



The apartment was one of many detours in an extended distribution chain that saw guns and drugs making their way to the Folk, one of the rare criminal organizations that \emph{predated} capes and still functioned in more or less the same fashion today.  Topsy and his underlings were guarantors, middlemen who made it possible for diehard enemies to do business.  If a fight erupted, he and his minions would deal with the situation quickly, promptly and efficiently.



It was a simple job, and it was one he'd done for nearly a decade.  In the process, he'd apparently grown exceedingly rich, and he had recently started to become more ambitious.  Campanile and Shuffle had interfered with a deal, and Topsy had hired some mercenaries to seek out retaliation.  If the escalation of the situation wasn't bad enough, the mercenaries had crossed lines, and Topsy had been relocated to the heroes' shit list as a consequence.  He was an acceptable target.



The only thing that would make Campanile and Shuffle happier than us fucking up and giving them an excuse to step in would be a perfectly executed operation and a humiliating loss for Topsy.  I'd do my best to oblige on that front.



Finding the way through the building's ventilation system was a question of mapping the system.  Once I knew the way, the bugs abandoned the map and made their way into the apartment.



I could have gone on the offensive right away, but this wasn't a conventional attack.  Every step of this had to be considered, measured, and plotted.



Minutes passed as I followed Topsy's movements through the apartment.  One by one, I collected his underling's phones, as they put them down.  A girl in the group said she needed to make a call, couldn't find her phone, and borrowed one from someone else.  The second she put it down and turned her back, cockroaches swept it into the space between the table and the wall, and then proceeded to nudge it well out of reach, beneath furniture.



Topsy's phone was the only one left, and he wouldn't put it down long enough for me to claim it.  I focused on the front hall instead, bugs collecting around jackets, boots and the winterized costume pieces, complete with warm coverings.



I could sense Annex and Cuff through the bugs that were warm and safe in the folds of their costumes.  They trudged through the two inches of snow that had accumulated on the plowed sidewalks.  Cuff seemed oddly more comfortable compared to Annex, who clutched his cloak around his shoulders.



``Annex, Cuff, I'm half a block up and to your right,'' I said, one finger on my earpiece.  ``Look for me in the lobby.''



``Got it,'' Annex reported.



Back to the preparations.  The goal here wasn't to defeat Topsy, but to \emph{break} him.  Part of the goal, anyways.



Silk lines tangled zippers and bound laces.  Gloves, both the ones for costumes and the ones for regular winter wear, were knotted with more silk, or they became home to wasps, cockroaches and millipedes.



Bugs too large or too small to be crushed found their way into boots.  Cockroaches bit and chewed at the finer straps that held the inner lining of jackets against the exterior.  The bugs I'd laced with capsaicin were relatively few in number due to the fact that it would kill the bugs next to them in the box, but I didn't need a lot of the stuff.  I transferred some to scarves and balaclavas by rubbing their bodies against the fabrics.



Annex knocked on the glass door, then melded into it and passed through before I could approach to open the door.  He rubbed at his upper arms as he opened the door for Cuff.



``You okay?'' I asked.



Annex only nodded.



\emph{There}.  I snapped my head up to look in the direction of the upstairs apartment, as though I could see through the walls.  Topsy had put his phone down on the kitchen counter to grab a beer, setting the thing to speaker mode while he looked for a bottle opener.



Bugs from the front hallway of the apartment flowed into the kitchen and swept the phone into the half-full sink.  Topsy didn't notice right away.



``Creepy when you do that,'' Cuff said.



``Hm?''



``Zoning out.''



``I've disabled their communications,'' I said.  ``Let's go.''



I moved the empty box to a corner of the lobby, hidden in plain sight, then led the way out of the building, with Cuff and Tecton following me into the adjacent alleyway.



Topsy was swearing as he nearly dropped his beer in his haste to rush to the sink and push his sleeves up to dig for the smartphone in the mess of dishes and scummy water.  I could \emph{taste} how much old food was in the water.  It wasn't a sense that translated well, but I could detect a thin, strong scent permeating the kitchen, one a select few of my bugs were attracted to.



``Tecton, Grace,'' I said, ``Annex and Cuff are here, we're standing aside while I engage.  I'm not forcing this.  Longer it takes them to catch on, the better the psychological effect.''



``Roger you,'' Grace answered.



It was all about thinking a step ahead.  I sent bugs into the room with the money and drugs and set them to destroying the plastic bags and eating through the paper bands of money.  Wasps and other hostile bugs nestled in the gun cases and around handles.  I didn't have many bugs to spare, so I used the others from the building that I hadn't deployed to make warning signs for the residents.



All in all, I managed about five or six minutes of quiet, steady destruction before one of the underlings walked in and saw what was happening.  I rewarded him by flying two capsaicin-laced insects into his eyes.



``They're sounding the alarm,'' I said.  The thug was hollering, and Topsy was shouting something about calling for the reinforcements, directing some swear words at the fact that nobody apparently had a working phone on hand.



That swearing swiftly became a stream of curses aimed at `that fucking bug bitch'.



``Annex, inside,'' I said.



``Good,'' Annex said.  ``Because I \emph{just} stepped outside, and now I'm going back in.  It's a pain to move through walls this cold.  Sucks the heat out of me.''



``Warm up inside,'' I said.  ``Take your time, but try to move upstairs.  Keep your head poked out so you can hear me.  I'll let you know what route they take.''



``Right,'' he said, reaching into the wall.  ``Fuck, that's cold.''



Then he was gone.



My swarm continued to plague Topsy and his people.  I slowly escalated the intensity of the attack, until Topsy gave the order to retreat.



``Get what you can and get the fuck out,'' Topsy ordered, ``Yeah, you too.  I'm paying you, aren't I?  Go find the bitch.''



Not so cheery for a guy with a playful name like `Topsy'.  Then again, I'd caught him at the end of his work day.  By contrast, I'd woken up, donned my costume and started my stakeout.  Eight hours, starting at four, watching and following as Topsy and his men conducted their business.  He was more tired than I was, and he was both a little drunk and a little high.



It meant he was a little more likely to freak out when their outdoor clothing turned out to be festooned with stinging, biting insects, falling to pieces or too entangled in silk to use.



``Bitch!  That bitch!'' the girl in the group cussed.



They knew who I was, apparently.  Fame had its disadvantages.



``Get downstairs, carry everything.  I'll bring the rest.  We'll take the trucks,'' Topsy said.



I smiled a little, ``Cuff, garage entrance.  Spike strip.''



``On it,'' she said, disappearing out the front door.



Once the majority of his underlings were out of the apartment, Topsy leveraged his power, reorienting gravity to shift the boxes and piles of stuff.  They hit the wall, slid down the hallway, and finally tumbled through the open front door of the apartment in a heap.  With money bands cut and bags chewed open, much of the merchandise in Topsy's stock was scattered to the wind.  My bugs could sense the clouds of powder filling the air.  Evidence, if nothing else.



He wasn't screaming, now, which I found odd.  Now that his underlings had gone ahead, he'd settled into a grim and quiet attitude.  He turned to the sole remaining underling.  ``Anything?''



``Too far to see,'' the man said.



``Keep looking as we head down.''



Topsy was tricky.  Part of the reason for the surveillance had been to identify the other parahumans in his group.  He hired mercenaries, paying well, and there was no sure way to tell who he had with him, short of seeing them in costume.  Trouble was, his people were defaulting to heavier clothing over their costumes, due to the cold weather. Identities were doubly hard to discern, and Topsy wasn't one to blab over the phone about who was working for him.



``Annex,'' I said, touching my earpiece, ``They're heading for the stairwell.  Do what you can, but let them keep moving forward.''



``\emph{Got it}.''



I sent bugs ahead of the group to check the way.  Annex flowed up the stairs to intercept them.  Some steps became slopes instead, others had the supports removed, so the stairs collapsed underfoot.  Each of Topsy's underlings fell at some point, their burdens thrown from their arms or crushed beneath them.  An unlucky or clumsy few fell more than once.



``Annex,'' I said.  No use.  He was inside the stair's surface.  An unfortunate side effect of his power was the fact that his senses were limited while he was inside an object.  He was blind, deaf, and his ability to \emph{feel} was limited by the material he occupied.  He could sense heat as much as the object could hold heat, could sense vibrations as much as the material could receive them.



``Annex,'' I tried again.



``\emph{I'm here.}''



``Back off.  They're catching up to you, and Topsy's on his way down with an avalanche of stuff.''



``\emph{Right.}''



I could see Cuff returning.  She saw my hand at my ear and didn't speak, giving me a thumbs up instead.



Annex spoke, his voice low, ``\emph{Okay.  I'll take a detour, fix the damage I did to the stairs, then rendezvous.}''



Very calm.  Assured.  It wasn't even something we'd plotted out beforehand, but there was no urgency here, no panic or distress.



Not on \emph{our} end, anyways.



Topsy's crew reached the first floor of the basement, which included the parking garage.  Topsy followed right after with the piles of goods, abused by their rough tumble down a dozen flights of stairs.  The packages of powder virtually floated in the air, with Topsy batting them in the direction of his people.



``Everything with red tape is highest priority,'' Topsy said.  ``Load it into the trucks first.  We can take a loss on the rest, pay the fucks back and claim intervention of bug bitch.''



``Two trips,'' the man I took to be Topsy's lieutenant said.  ``Bug girl can see what her bugs see.  She'll be on our heels.''



\emph{I'm not even fifteen paces away}, I thought.  I'd worried they would exit at the ground floor, but it was safe.  I made my way inside to grab my insulated box.  \emph{Heavy}.



The lieutenant continued, ``Mockshow, open the garage doors.  Get some cold air in here.''



``I'm already freezing,'' the girl of the group said.  ``We left our jackets up there.''



``Don't fucking care.  Bit of cold will deal with these bugs faster than it hurts us.  \emph{Move}.''



Mock obeyed, while the others loaded up the trucks.



``Be advised,'' I reported, my hand to my ear, ``They're attempting retreat in vehicles.  Original plan may hit a snag.  Topsy's got a newbie supervillain working for him.  Mockshow.  If I'm remembering right, she's a master-slash-shaker six.''



``\emph{Roger},'' Tecton said.



``\emph{Hold on},'' Grace said.



Mockshow touched the garage door, and the mechanisms shifted to life.  Cold air flooded into the garage.  I was forced to pull my bugs back, drawing them into the stairwell and through the vents to the box I held.  Only the bugs nestled in the villains' clothing remained.



I could barely hear as the lieutenant spoke to Mockshow, ``\emph{See}?''



``\emph{Bosses are advising we try plan as detailed},'' Grace said.  ``\emph{If it fails, orders are to abort.}''



And there was our first bit of interference.  The Director didn't want us to succeed.  Topsy wasn't a likable guy, was dangerous in his own way, even, but he was a known quantity.  Manageable.



\emph{Fuck that}, I thought.  \emph{I didn't sit in the snow for eight hours, bored to tears, to have this  mission end at the first excuse.}



I didn't say it aloud.  I focused on what our targets were doing.



The trucks had apparently been loaded up, because the villains were gathering into three vehicles.  They peeled out with a squeal both I and my bugs could hear.



No less than ten seconds later, they ran over the chain that Cuff had laid in the snow just past the garage door.  She'd reshaped it so spikes jutted out, I knew.  I could hear the tires pop, and pieced together the scene from the movements of the people and boxes within the trucks.  The second truck had made it halfway across the spike strip losing its front tires, but the collision of the third truck ramming it from behind drove its rear wheels over the strip.



Two of three trucks disabled.



I stayed where I was, letting the last of my bugs finish gathering in the insulated box, then carried it outside to Cuff.



``Spiked chain worked,'' I commented, my voice a murmur.



Cuff pumped a fist.



I touched my earpiece.  ``Two cars disabled and a third trapped behind.  They-''



``Watch,'' Topsy said, as he climbed out of the truck.



Not a statement.  A name.  I felt my heart sink a touch.  Of all the motherfucking people he could have hired-



``What?'' his lieutenant asked.



``They've got to be close.  Take a second, look for them.  Mockshow?  Get us moving.''



It didn't take Watch two seconds to turn and face the alley where Cuff and I were hiding.



``\emph{It's Watch},'' I whispered, ``\emph{They're on to us.  Go.}''



Cuff nodded and reached for her left ear.  I seized her wrist to stop her.



She gave me a funny look.  ``Mission's a bust.''



``Mission is on,'' I hissed the words.  ``Go.''



I lifted the box, as Watch and Topsy made their way up the snow-covered ramp to us, underlings following them.  An adjustment of gravity removed the issues the slope posed.  Watch was saying something I couldn't make out over the rush of wind.  Something about our location.  We didn't have long.



Watch was a package deal like Grace or Circus.  A lot of powers, flexible.  His specific powers weren't on record, but it was fairly well known that he was capable of short bursts of intense, short-ranged clairvoyance.  He could see people's biology, ignore the issues of light, darkness or intervening objects, and he had a limited super speed coupled with what had been dubbed `phantom hands'.  The ability to reach through people like Shadow Stalker might, targeting particular aspects of people's body to shred arteries or tear through nerves with his fingers and fingernails.



He was a monster who left his victims dead if they were lucky, quadriplegic if they weren't.  Maybe that was ableist, but I didn't fancy being left to rely on the care of others for the rest of my natural life, suffering what was, by all accounts, an indescribably painful case of phantom limb.



It said a lot about Topsy and the direction he was taking his enterprise, that he'd hire this bastard.



I nearly dropped the box, slick as it was with the snow that had melted while it sat in the lobby.  Cuff helped me catch it.  A moment's delay, but enough time for Topsy, Watch and the others to crest the top of the ramp that led from the basement level to the street.



As we ducked behind cover, taking our steps into the alley, the snow that had accumulated on the ground began to fall in reverse, in thick, wet clumps.  I felt the same kind of lift that accompanied a use of my flight pack, and both Cuff and I were lifted off the ground as well.



The weightlessness ceased, and we fell.  Only we fell \emph{up}.



My flight pack kicked to life, and the wings unfolded so I could use the propulsion.  I reached for Cuff with one free hand, nearly grabbing one of her braids, but found her wrist instead, felt her hand clasp my wrist in return.  Snow and ice pummeled us as it broke free of the sidewalk and flew skyward.



It also, I noted, helped to obscure us.  Some gunshots sounded, though we were safe around the corner.



With the flight pack, I managed to steer us towards the fire escape, throwing the box down -or up- and seizing a handhold.  I found a grip and started to swing Cuff towards the railing when gravity shifted again.  Cuff jerked, and I found myself half-folded over the railing, trying to keep her from falling through the open mouth of the alley and into Topsy and Watch's sights.



Her legs dangled towards the street we'd just left, and I couldn't muster the upper body strength to lift her.  Worse, her grip was too tenuous for her to risk letting go to climb up my arms and shoulders and reach safety.  Her right arm still wasn't as strong as it should be.



The arms of my flight pack reached out to try and grip Cuff, but the angles of our bodies didn't offer anything substantial to grab.  Her braids?  No.  Nothing on her costume either.



The chain looped around her back?  Yes.



``Chain,'' I gasped the word in the moment her gauntlet slid from my grip.  The insectile arm at the side of my flight suit snagged the chain and passed it to my hand in a sudden, jerky motion.  She caught the lower half of the loop and jolted to a stop, her lower body dangling out in sight of Topsy and his men.



They opened fire, and Cuff shrieked in alarm.



Not quite so calm, leisurely and confident, now.  \emph{Damn it}.



Still, we managed to reel her in, her climbing, me hauling the chain in, inch by agonizing inch.  The men with the guns rounded the corner, still shooting, as they kept out of the way of Topsy's power.  I had to duck low to take some cover behind the insulated metal box and the metal slats of the fire escape.  More bullets ricocheted off of Cuff's armor.



She found the railing, and I gripped her armor to help pull her over.



``\emph{Getting reports of shots fired,'' }Grace said\emph{.  ``Bosses are worried.''}



\emph{Fuck the bosses.  }``All good,'' I responded, injecting calm into my voice.  ``We weren't in danger.  They're ticked and shooting indiscriminately.''



``Roger,'' Grace said.  ``Be safe.''



``Not in danger?'' Cuff practically snarled the question at me.  It was out of character for her, but that was excusable considering she'd just been shot at.



``You're bulletproof.  \emph{I'm} bulletproof, even.  Between the new Darwin's bark spider silk costumes, and your armor, you were safe.''



As if punctuating my statement, a gun went off below, making the railing sing with the impact.



``Annex,'' I said, communicating using the earpiece.  ``I can sense your location.  Climb two stories and give me an exit on the north face of the building.''



``\emph{Which way is north?}''



``Your left.''



``\emph{Gotcha.}''



``The way you worded that\ldots'' Cuff said.



``You're not coming with,'' I told her.



Gravity shifted again.  Our backs slammed against the side of the building, the two of us grunting in unison.  My metal box scraped against the metal of the fire escape to land beside me.  We were now more or less lying down on the building's face.



Watch and Topsy's men were making their way along the side of the building, walking on it.



I pulled off my flight pack and handed it to Cuff.



``I don't know how to fly this,'' she said.



``\emph{I'll} fly it,'' I told her.  I noted the hole Annex was making.  ``Go over the top of the building to the roof.  \emph{Fall}.  It'll take you out of range of Topsy's power, you'll be returned to a normal orientation.  Drop again, off the other side of the building, sneak around and stop Mockshow.  If she gets the group moving, we won't be able to intercept and carry out the plan.''



``We're supposed to report if we run into trouble, cancel the mission.  This is a \emph{lot} of trouble.''



``Trust me,'' I told her.  ``Please.  Go fast, before Watch catches up.''



She nodded, and I gave her a boost with the flight pack to move her along as I dropped into Annex's hole.  I made it ten feet into the hallway before getting out of range of Topsy's power and skidding to a halt on the carpeted floor.



Cuff sprinted for the ledge that was the rooftop.  She fell only three or so feet before gravity reasserted itself, driving her into the snow and gravel.



I noted Mock, but I couldn't see much of what she was doing.  Her power, though, put her in the same general category as Rachel.  She empowered minions.  They even fit into the same general weight class as Rachel's dogs.  The difference, though, was that they were inanimate.  Loose, telekinetically animated servants, typically with the size, clout and general strategy of a grown rhino.  Charge things, hit them hard, repeat.



I had no doubt she'd be working on the truck.  Maybe multiple trucks.  Bugs were still inside the vehicles, and I could sense things shifting and lurching as she reconfigured it into a more or less mobile form.



Watch was suffering with both the winter weather and his lack of proper footwear.  He was fast, but the terrain was slowing him.  Ice and snow had been thrown against the side of the building by Topsy's power, and every other step threatened to send Watch tumbling.  His super speed wouldn't help him much when he had to plot his movements like this, but it still made him incredibly dangerous if he did get one of us in reach.



He crested the top of the building as Cuff reached the other side of the roof and jumped down.



Propulsion and antigravity together weren't enough to slow her fall.  A miscalculation.  She was too heavy, with her armor.



I promised myself I'd owe her one and slowed her the only way I could – I used the flight pack to push her against the side of the building, using friction and drag to slow the fall.



She hit the alley on the far side of the building at a speed that was probably too fast to be comfortable, not so fast she was gravely hurt.  I used the propulsion in the flight pack's wings to help speed her along as she stumbled, jogged, then sprinted towards the front of the apartment building.



Cuff rounded the corner just as Mockshow led her quadruped truck-minion outside.  I folded the wings in just as she made contact.



Cuff could use her short range metallokinesis to manipulate her armor, effectively granting herself increased strength.  She could, it seemed, also use it to impact the metal she was \emph{hitting}.  She wasn't moving \emph{that} fast, but everything my limited senses could tell me suggested she delivered a hit like a freight train striking a car that had stalled on the tracks.



``No!  Fuck no, fuck damn!'' Mockshow shouted.



Cuff threw out a chain with an audible clatter, then caught the end, moving like she was winding it around the villain.  She reconsidered as Topsy and his minions reacted to the noise of the collision and came after her.  She was nearly at the far end of the street when Topsy used his power.  He reoriented gravity, and she veered to one side, striking the wall beside the alleyway rather than disappearing inside.  The tilt continued, and she turned away, moving with the tilt.



He leveraged his power further, only this time, it was his namesake topsy-turvy `up is down' variant.  It was his most offensive power, the ability to hurl large numbers of people or objects into the city's skyline, then revoke his power to let them fall.



Cuff, to her credit, was ready.  I could sense her catching ahold of the building's face, using the cover of the rising snow around her to climb up and disappear into the alley.



``\emph{Status, Weaver?}'' Grace's voice came over the channel.



``All kosher,'' I replied, managing to sound calm.  I walked to the far end of the hall and turned a corner, until I stood by a window with a view of the villains.  ``Waiting to see which way they go, so sit tight, Golem and Tecton.''



``\emph{Fuck},'' Topsy was saying, as he approached the wreckage.  Mockshow was using her power to animate the chain and help herself out of it.



``What the \emph{hell} was that?'' Mockshow asked.



``Wards.  \ldots this, it's a trap,'' Watch said.  He'd made his way back down the side of the building, where Topsy's power had oriented gravity at a right angle.  He was calm as he spoke, ``They shut down this \ldots area, and they're making \ldotscal strikes to disable us.  Even the fact that \ldotsshow here doesn't have a \ldots and I'm wearing sneakers instead of boots, they wanted that.  They want us unprepared, angry, even \emph{cold}.''



``I'm paying you to get me out of this kind of situation,'' Topsy said.  ``Do your job.  How do we handle this?''



``They want us pissed enough to fight,'' Watch said.  ``Don't.  Also\ldots yeah.  Bug bitch tagged us.  Here.''



He reached for Mockshow, and she slapped his hand away.  He caught her wrist, simultaneously capturing her arm and blocking the path of the cockroach I'd hidden in between her sweatshirt and her jacket.  He plucked it out.



``Ew!  Ew, ew!''



With a systematic, accurate and \emph{patient} series of movements, Watch began catching and killing every single one of my bugs.  Slowly but surely, I was being rendered blind and deaf.  It would make tracking a great deal harder.



``Cuff,'' I communicated over the earbud, ``Let me have the flight pack.''



Dutifully, she unhitched the harness and let me pilot the thing back in my general direction.  Annex and I made our way outdoors, back to the fire escape, as Watch killed the last bugs.



``Ew, ew, ew,'' Mockshow moaned, with each bug that was revealed.



``\ldots \ldots think we should fight?'' Topsy asked.  ``\ldots \ldotsing kids.  \ldots money, my rep\ldots''



``Could fight,'' Watch said.  ``\ldotsther plan.  Let me kill these last few, then I'll \ldots''



Over the ensuing four or five seconds, he killed the bugs I'd planted on him despite my best effort to retreat them to inconvenient and inaccessible areas.



My flight pack returned to me, and I strapped it on, before flying to the roof for a better vantage point.



``Going to be hard to track,'' I reported.  I could see them running.  ``Watch killed my tracking bugs.  They're heading north, along Addison. roughly four hundred feet away from my location.''



It was Revel's voice, not Grace's, that came over the channel.  ``\emph{Watch?''}



``With Topsy and Mockshow and five underlings with guns and no apparent powers.  They're on foot, trucks are disabled.  Can I get a roger?''



``\emph{Roger},'' Tecton said, ``\emph{Moving to intercept with Golem.}''



``\emph{Belay that},'' Revel cut in.  ``\emph{I'm not throwing my Wards to the wolves like this.  Abort.  Protectorate moves in.}''



``You let them face Behemoth,'' I said.



``\emph{Different story}.''



``We're \emph{safe},'' I said, taking flight to keep my eyes on the villains.  ``There' \emph{more} danger if you derail the plan.  They won't even \emph{see} us.''



``\emph{Watch sees everything},'' Revel answered.  ``\emph{Everything within range of conventional eyesight, from every angle.}''



``Revel,'' I said.  ``We won't get close to him.  Promise.  I've been on the team for six months, I've shown you guys I can play nice, play safe, avoid making trouble.  But you guys brought me on board to be the shot caller in the field, with Tecton as the \emph{leader}.  Let me do what I'm supposed to do and call the shots.  It'll be a win for the good guys, I promise.''



There was a long pause.  \emph{I'm up against Revel and the Director, now}.  My advocate had switched stances.



I took flight again to maintain a good distance.  I wasn't sure, but I thought maybe Watch had briefly turned my way.



He knew I was following, but he didn't seem to mind.  He had a plan.  Maybe more than one.



They wasted no time in putting it into action.  Topsy used his power over a wide area, reversing gravity's effect.  Snow began to fly in the air, and was soon joined by a pair of cars.  They reached the top of Topsy's effect, caught between the two gravities, and began to rotate aimlessly in the weightless middle-ground between normal gravity and the area Topsy had altered.



Then he shifted gravity's direction again.  An attack, such as it was.  The snow and cars fell in \emph{my} direction.  Were flung, for lack of a better term.  I flew for cover, ungainly as I raised the insulated box as a shield, snow and ice slamming into the buildings around me, pinging off of the metal.  I managed to duck out of sight.  The cars, for their part, were only thrown into the street a block away.



It wasn't an attack he'd \emph{aimed,} but a scattershot approach, meant to scare, to allow the possibility that he'd get lucky.



And it had given them the chance to try and slip away.  A few minutes, while I recouped and tried to get my sights on them in the midst of the stirring snow and limited visibility.



``\emph{Okay},'' Revel said.  ``Only because we can't move the Protectorate heroes there fast enough.  You are \emph{not to engage.''}



``Roger,'' I reported, my relief mixed with a frustration that the go-ahead had come so late.



Their attempt to occupy me and break away might have worked, if it weren't for Golem and Tecton.  The villains had come to a complete stop as they reached the barrier.  A row of asphalt and concrete hands, the gaps filled by Tecton's power.  The wall was as tall as the buildings on either side of it, spanning the breadth of the street.



Topsy began to use his power, moving snow at the far left of the wall, no doubt intending to scale the structure, move over the wall.  Watch stopped him.



They turned to run instead, moving parallel with the wall.



Watch, I guessed, had seen Tecton, Golem, and the two PRT trucks on the other side of the wall, ready to spray the villains with containment foam.



By the time Topsy and his crew reached the next street over, the PRT van had pulled to a stop.  Golem was outside the vehicle, creating another barrier.  The implication was clear.  Every escape route would be cut off.



This was a battle of attrition, a \emph{patient }fight, with civilians kept out of reach.  We'd let them get tired, frustrated, cold, and we'd break their spirits.



The goal here wasn't just to \emph{win}.  It was to win so irrevocably that we took the fight out of them altogether, left them without any hope that they could win the \emph{next} time.



Topsy hit Golem and the truck with flipped gravity.  Both moved, but neither lifted off the ground.  Even before he started raising the wall, Golem would have used his power to hold his feet against the ground, to grab the truck's axle.  Tecton would be waiting inside, ready to leap out and break the hands if necessary.



The villains could have continued.  In their shoes, I might have.  It made sense, to force Tecton and Golem to stop and start until an opening presented itself.



Except they were cold, tired, and being countered at every turn was starting to take a psychological toll.



They might have split up, scattered, but they didn't.  Again, they suspected a counterplan.  Which we \emph{did} have.  Golem and Tecton could have tripped up the most problematic combatants while the rest of us picked off the weakest members one by one.  I didn't have bugs, but I could fly, and I had coiled lassos of silk cord that I could use in a pinch, along with a taser that I could use if I wanted to end things sooner than later.  A good attack from above, I could manage.  If they went inside, I could unload the bugs I had in my insulated box.



They had a different plan in mind.  They reversed direction and headed straight for a restaurant with a sign showing a gold dragon against a red background.



``Grace,'' I said.  ``Wei shu wu?  Does typing it into the computer turn up anything?''



``\emph{A cover business for a group with affiliations to the Folk},'' Revel volunteered.



``We safe to harass them, or-''



``\emph{No.  They have people with powers, and that's beyond the scope of this manhunt.}''



``Can you find the number at the building?  A restaurant, Wei shu wu.''



``Weaver,'' Revel said, her tone a warning.



``Please,'' I said, as the villains disappeared inside.



Revel only sighed.



A moment later, the phone rang, and I could hear a voice.



``\emph{Wei shu wu dining.  Would you like delivery?  We can also arrange reservations if needed.}''



``We would, if it's no trouble,'' I said, hoping I was connected.  ``Eight criminals just entered your restaurant on Addison.  They're cold, bedraggled, a little desperate.  It's an ugly situation, and I'm sorry for the trouble that's found its way to your doorstep.''



``I'm not sure I understand.''



\emph{Playing dumb?}



``It was trouble they started,'' I said.  ``They crossed lines, and now that we're coming after them, they've come running to your place for shelter.''



``We can hardly offer anyone shelter.''



``I know,'' I said.  ``But call your boss, if you need to.  Let them know that the heroes aren't going to start a fight, but the villains inside the building need to leave and get taken into custody.  If this goes any further, we're not going to press you, but it's going to draw attention.  People will wonder why the bad guys are hiding there.''



``\emph{Weaver},'' it was a man's voice this time, over the comms.  ``\emph{You don't have the authority to make promises or offers.}''



``\emph{We can't make them leave},'' the man from the restaurant said, his voice a whisper.  ``We don't have ability to make threats.''



\emph{Because you're hapless restaurant owners or because your gang doesn't have the clout there to go head to head with Topsy?}



``Don't hang up the phone,'' I said, ``Use your cell phones, talk to anyone you can think of that might help.  Bosses, franchise owners, whoever.  Fill them in.  Let them know that the guests in your store include men called Topsy and Watch.  If they ask who I am, you tell them I'm a superhero called Weaver.''



``From the video?''



``From the video,'' I said.



His tone changed, as if he'd shifted mental gears, at that.  He sounded vaguely plaintive.  ``You're talking as if my boss is an important man, but-''



``You're just a restaurant employee,'' I said.  ``I understand.  Call whoever.  We'll figure this out together.''



There was a muffled sound, as if he was covering the phone's mouthpiece with his hand.



``\emph{You're talking as if you're on the same side},'' the man said.  The Director, I was pretty sure.



``\emph{Weaver},'' Revel chimed in, sounding annoyed.



``Mute me so he doesn't hear?'' I asked.



``Already done,'' Revel said.  ``This isn't the way we should do this.''



I bit my lip.  I wanted to retort, to argue, but I knew there were too many listening ears.



\emph{This is exactly what we should be doing}.



``They're people,'' I said.  ``They're bad guys, maybe, but they're all people.  Topsy and Watch and Mockshow want the same things we do, to be safe, warm, dry and well rested, and we're taking that away from them.  And the people who work with this restaurant?  They don't want to deal with people like Topsy and Watch.  All we have to do to resolve this is make it easier to deal with \emph{us} than to deal with the other villains.''



``\emph{We shouldn't be dealing with them, period},'' the Director said.



``We-'' I started to reply, then I stopped.



Topsy, Watch and Mockshow had stepped from the building.



``They just decided to leave,'' the restaurant employee said.  His voice shook a little.



I could see the body language of the three villains and their henchmen.  Topsy kicked the window at the outside of the restaurant, and a crack appeared in it.  He shouted something I couldn't make out from my vantage point.



\emph{I'm sure they did}, I thought.  But I only said.  ``Thank you for cooperating.''



``Thank you for talking me through this,'' the man said.



With that, he hung up.



\emph{Something} had gone on that I hadn't overheard.  An exchange of words, a message from the Folk?



It didn't matter right now.  I watched as the villains made their way down the street, then broke into a store to find shelter from the cold.



It was over.  I could read it in their body language.  As much as the Director had wanted to wear me down, to have me sit in the cold with nothing to occupy myself with but the five minute check-ins, we'd achieved the same thing against the villains, and we'd been successful in doing it.  This was only residual stubbornness.



My arms were stiff with the weight of my bug box.  I was glad to set down on the roof and deploy the bugs, flooding the building and driving the villains out into the elements.  They had winter clothing they'd stolen, but it wasn't enough to restore the warmth they'd already lost.



By the time they found more shelter, Annex and Cuff had met up with a PRT van and been delivered to the scene.  Annex approached from behind, slithering close, and then used his power to open up a closed storefront, allowing cold to pour into the building's interior.



This time, when the villains emerged, they did so with arms raised in surrender.



``We did it,'' I muttered.



``\emph{Be wary of Watch},'' Revel said.  ``\emph{Containment foam him first, then move him to a truck.  Good job, Wards.}''



\sectionbreak



I watched Mockshow on the monitors.  She was young.  Well, young was relative.  She was fourteen or so, and now that she had her costume with her, she wore a hard mask sporting a stylized smiley-face, a headband with screws sticking out like antennae.  She'd lost the outdoor clothing and had donned her mask, as if it were a shield between her and us.



I glanced over at our superiors.  Revel was in a discussion with the Director, the Mayor and the police chief.



Mockshow's eyes widened as she saw the bugs filtering into the interrogation room.  The tables and chairs had been removed to deny her anything solid enough to use her power on, so she had nothing to hide behind as they began forming into a mass.



``Aw hell no,'' she said, as she backed into a corner.  ``No, no, no, no\ldots''



They gathered into a rough humanoid shape.  My shape.  A swarm-clone.



``No!'' she shouted, as if her refusal to accept it could banish the thing from existence.



``\emph{Let's chat},'' I communicated through the swarm.  ``\emph{Off the record.}\emph{``}



``Screw you!  Driving me out into the cold, fucking with us without a fair fight?  Go die in a fire!''



``\emph{I've been in a lot of fights,}'' I commented, ``\emph{Rare to have one that's actually fair.  Most are pretty brutally one sided.}``



``Do you not hear me?  Screw yourself!''



The swarm advanced a little, and she shrunk back.



``\emph{Paradigm is changing, Mockshow.  I want to make that clear, so you know what people are talking about when they offer you deals.  People aren't going to be inclined to play nice}.''



``\emph{Nice}?''



``\emph{The three strike rule, cowboys and indians, counting coup\ldots}``



``You're cracked.  The fuck are you talking about?''



``\emph{It doesn't matter.  Things are shifting.  People are relaxing when they shouldn't be, because Behemoth died, and-}``



``Pat yourself on the back more, why don't you?  I saw that video.''



\emph{Everyone did}, I thought.



I couldn't let her get me off topic.  ``\emph{I'm going to tell you what I would've wanted to hear if I found myself in your shoes, at this point in time.}``



``Oh, \emph{so} generous.''



``\emph{There's two groups of people.  There's the people who're preparing for the end of the world, who are on pins and needles waiting to see just what hits us next, how the dynamic's going to change.  I'm in that group, understand?  In my book, in our book, anyone who isn't keeping the peace and isn't helping doesn't deserve any mercy.  They're detriments.  You're dangerously close to falling into that category}.''



``Whatever.''



``\emph{And the other group?  They're the people who've finally found a glimmer of hope, and they're relaxing, thinking maybe we can take out the remaining Endbringers, maybe the world can go back to normal.}``



She snorted.



``\emph{Yeah.  Exactly},'' I said.  I glanced at the others.  The Director wasn't participating in the conversation anymore.  He was staring at a monitor, but his reaction didn't suggest he was watching me interact with Mock.



Either way, I had to wrap it up.  ``But those guys?  They aren't on your side either.  Once upon a time, they'd be the same people who'd push for people like \emph{you} to go free.  Because maybe you'd help somewhere down the road.  Now?  They have no reason to give you that slack.  You've got no help here, and I think you'll be surprised at how hard they come after you.''



``I didn't do shit.  I've barely had my powers a \emph{month}.''



``You signed up with Topsy.  With Watch.  This is as much about them as it is about you. Making \emph{Topsy} uncomfortable, denying him a resource they'd just acquired.  Stripping away his conveniences, leaving him wondering if you'll plea out.''



``Fuck that.  I'm good.  Not saying a word.''



``Probably,'' I said.  ``But take it from someone who's been there.  You don't want to go down this road.  The heroes will come after you hard, the villains will never trust you.  Honestly?  I don't care if you stay a villain or become a hero.  But it's not worth it to be a villain and stick with guys like Topsy.  The gains aren't worth what it costs you.''



``I turn traitor and walk away, I'm fucked.''



``Join the Wards,'' I suggested.



I experienced a momentary flashback to my first night out in costume, talking to Armsmaster.



\emph{Holy shit, have I become him?}\emph{Pursuing my agenda, offering the options I know she won't take, steering her towards my self-serving goal}?



It chilled me, bothered me far, far more than Mockshow's snort of derision.



``Or go be a scumbag, but be a scumbag who helps save the world,'' I said.



She rolled her eyes.



``Us or them, Mockshow,'' I told her.  ``Saving the world or getting in the way.  If you're helping, we pull our punches, the charges don't stick, whatever.  You get in the way, well, every night can be like tonight was.''



She scowled.



``That's all.''



``Fucking rich.  You're just pushing me to go join your old team.''



``I'm suggesting that you consider your options.  Pay fucking attention to where you're going.  I wish I had.  That's all.  If you want to contact me, that door will be left open.  I'll pull strings to make sure of it.''



``I gotcha,'' she said.  Her shoulders slumped a little, as if in defeat.  She glanced up at me, and I could see a glimmer of vulnerability in her expression.  ``Weaver?''



``What?''



``Can I ask you something personal?''



``Yes.  Of course.''



She opened her mouth, then closed it.  She stuck her hands in her pockets, then glanced at the windows, which were partially obscured with half-closed blinds.



Finally, she spoke.  ``Would you please, \emph{please} go fuck yourself?  Upside-down and backwards?''



I sighed, dissipating the swarm.



I felt my hair stand on end as the Director approached.  I'd always felt a little caught off guard by him.  He looked more like a classic politician than the generals and soldiers I was used to associating with the PRT, with dimples, styled sandy hair and a tidy suit.  His demeanor, body language, everything, it was \emph{warm}.  That warmth didn't reach his eyes.  Not when he'd looked at me.  Especially not right now.



He'd seen the swarm-clone in the interrogation room.  I knew it.



For long seconds, we stared at each other.  I'd thought he would say something, but he didn't.



``Thanks,'' I said, ``For playing ball.''



``I didn't.''



``You could have made that harder.''



``Making it harder would have done more harm than good,'' he said.  ``I've still got two teams to run, a specialized police force to organize.''



``Yeah,'' I said.



``Mockshow.  Was she receptive?''



I shook my head, but I said, ``Maybe.  Maybe something will sink in.''



``Teenagers have a way of being bullheaded,'' the Director said.  ``Villains too.  Teenaged villains?  Well.''



His eyes didn't move one iota away from me as he said it.  It left no question about how he'd compartmentalized me in his head.



``I suppose you're right,'' I said.



``Having Topsy off the streets is going to be a feather in a few caps, I think,'' he said.  ``It's messy to credit you.''



``I really don't care,'' I said.  ``I just want to make some steps forward in this mess.  Prepare for the worst.''



He studied me in a very slow, careful way, as though taking everything in.  Assessing the target.



``I could raise an issue with you being in that interrogation room.''



``Maybe,'' I said.  ``It'd look obvious, that you were coming after me.  I didn't say anything really problematic.  But it's an option.''



``You withheld details.''



``It's kind of crazy out there, in the midst of a fight.  You lose track of stuff.''



``I know,'' he said.  ``I used to be a soldier.''



That caught me off guard.  He didn't look like he'd ever been in a fight, let alone a war.  He was so young, too.



``You haven't been a cape for long,'' he said.



``A year.''



``A year.  But you've been through a lot.  I'd hope you were better about minding those details.''



A slap in the face, not calling me out on the fib, but turning it against me.



He seemed content with that for the moment.  He didn't press the offensive.  I didn't either.



``We both got what we wanted tonight,'' I said.  ``It's a win, isn't it?''



He didn't reply, glancing at the Mayor.  The man seemed happy as he talked to Revel and the police chief.  Not \emph{giddy}, but happy.



``Is this going to let up?'' I asked.  ``Or are we going to be fighting each other constantly?''



The Director glanced at me.  ``You want this to stop?''



``It's a waste of energy.  There can't be compromise?''



He didn't even have to think about it.  He shook his head, briefly pursing his lips.  ``No compromise.''



I clenched my fist.  Damn him.



``A balance,'' he said.  ``Maybe a balance.''



``What's the difference?''



``I think,'' he said, choosing his words carefully, ``That a compromise would be disastrous.  You're not going to be confined.  You showed that in the interrogation room in Brockton Bay, when you murdered Director James Tagg and Alexandria.  You're not going to be confined by \emph{law}.  I haven't seen a single case where you've followed the rules that were outlined for you.  Boundaries don't work, in any sense.  If we reached a compromise, worked out some kind of a deal, you'd find a way around it, extending your influence.''



``That's not fair,'' I said.



``It's reality.  It's a horrible waste of energy, a tragedy, really, but I'm forced to dedicate time to reining you in, controlling you, keeping you in check.  If that results in nights like tonight, we have a balance.  Hardly a \emph{compromise}, but we'll manage.''



``I suppose we'll have to,'' I said.



``I'd tell you to avoid leaking the fact that you played a major role in tonight's events, but we both know you wouldn't listen,'' he said.  ``I'd threaten punishment, but you'd do what you wanted and even \emph{enjoy it}, feeling vindicated.  So we'll go another route.  If you don't play ball and let us share this narrative the way we need to, I punish the other Chicago Wards.  Inconvenient shifts, extra volunteer work, more paperwork.''



``I told you, taking credit isn't a concern for me.  I've got other priorities.''



``Good,'' he said.  He flashed me a smile.  White capped teeth.  ``Good.  Then this is ideal.  We may not have a compromise, but a consensus?  It'll do.''



``It'll do,'' I said.



``Just do me a favor?  Try not to murder me like you did the other three Directors.''  He winked.



It was a jibe, a verbal thrust, delivered with humor and offhandedness, but it struck home, stirred ugly feelings.



He turned to rejoin the others.  The Mayor looked at me, and Revel waved me over.  I knew the Director wouldn't want me to, so I walked over with confidence, my head held high.



``\emph{Eight} hours?'' the Mayor asked.  ``Sitting in the cold?''



``Yes,'' I said.



``Is that even legal?''



The Director stepped in, ``It wasn't on the clock.  For all intents and purposes, she wanted to take the day off, have some time by herself.  We had the tracking device monitored by GPS, so we knew she wasn't going anywhere she shouldn't.  Being the workaholic she is, she wanted to get intel while she had her alone time.''



I didn't argue the point.  He wasn't \emph{wrong}.  That was how it was going down in the paperwork.  Part of the deal we'd arranged to get this off the ground.



The mayor smiled.  ``Well, good to see our most controversial member is doing her part.   You should smile more.  Can we get a smile out of you?''



I smiled a little.



``Better, better!  You do bide your time, then make a big splash, don't you, Ms. Weaver?''



He was managing to sound a little condescending, which was at odds with the events he was alluding to.  How did one make me sound so diminutive when making vague reference to the death of an Endbringer, to the murder of Alexandria and the takeover of a city?



I didn't mention it.  I had my pride, but it wasn't something worth fighting over.  I wanted to pick my battles, and any moment now-



``Hopefully we'll see more of the same from you in the future,'' the Mayor said.



The Director started to speak, deflecting, but I cut in.  ``Actually-``



Eyes fell on me.



\emph{Picking my battles}.  If the Director wanted this to be a war, if he thought I needed to be tempered by an opposing force, then I was game.



I glanced at the Mayor.  ``Tecton went over it with me, we've got more plans like we had for tonight.  If you guys are willing.''



``Willing?  I can't imagine why not!'' the Mayor said.  He smiled at Director Hearthrow, who smiled back.



The moment the Mayor wasn't looking, the Director shot me a glance, a dangerous, warning look.



\emph{I told you}, I thought.  \emph{My priorities are elsewhere}.



``How soon?'' the police chief asked.  Her stare was hard, judgmental, but there was curiosity in her tone.



``The sooner the better,'' I said.  ``Before they catch on about what we're doing and adjust.  I think I know where a few possible major players are situated.  I've spent the past few months looking for them.  I gathered the intel in my spare time, on my morning runs and patrols.  Just like Director Hearthrow was saying.  I'm a bit of a workaholic.''



``Like, two weeks?'' she asked.



``Give me a day to recuperate, maybe two days if the other Wards need it, I'd be down for another.  We could potentially hit seven or eight major targets in the next two weeks, if you wanted.  Each of them would be major targets, villains who aren't playing along, who are more trouble than they're worth.''



The Director shook his head.  ``I think that may be extreme.  The resources expended, funding-``



``Funding can be conjured up for a project like this,'' the Mayor said.  ``Imagine the impact.  Can we do this with the Protectorate team as well?  Switch off with the minors?''



``It's a good idea,'' Revel commented.  ``Weaver's capable of handling her own in high pressure situations, but the other team members might not be.  They have school, family, other concerns.''



``I agree,'' I chimed in.  ``Makes sense.  We could have the bad guys reeling.''



``We can't set our hopes too high,'' the Director warned.  He gave me another dirty look.



The Mayor chuckled.  ``No.  Of course not.  But the \emph{impact}.  And to do it with so little \emph{risk}?  They barely interacted with the villains, by all accounts.  It would be insane to pass up the opportunity.''



``Insane,'' Revel said, her tone flat.  I couldn't read her feelings on this.  I hoped I hadn't provoked her as much as I had the Director.



``If you're willing to allow me to suggest some targets,'' the police chief said, ``I think I could adjust shifts, ensure we have enough squad members to limit or stop traffic inside potential sites of conflict.''



It was consent, in the form of a negotiation.  The mayor and police chief were interested, Revel was probably on board.  The Director would be forced to play along.



It was done.  I was all set to hit the ground running, like Glenn had recommended.  Big moves.  Actions with momentum.  Here on out, I'd have to keep moving so they couldn't get me.



And hopefully, in the midst of this, we'd be able to organize things for our potential end of the world scenario.  Eliminate the obstacles, big and small, train up the rank and file troops.



If anyone thought I was cleaning up Chicago, they were wrong.  Like the Director had said, I'd take as much rein as they gave me, use all of the leverage and momentum I could get my hands on.  Topsy was a small fry in the grand scheme of things.  A test run.  I wanted to hit big targets in other cities.  To get as many Mockshows into the interrogation rooms as possible, to play the odds and increase the chances that we could get those people on the fence and make sure they were positioned appropriately.



The clock was ticking.





