





Touch\emph{\'{e}}, \emph{PRT.  }



You got me.



Touch\emph{\'{e}}.



``\emph{You're attempting to reach Glenn Chambers, co-president of Faceti.  For our mutual convenience, please categorize your message.  Press one to contact my personal assistant, who can get your message to me in text asap.  Press two if you got my number from my business card.  Press four if you are an employee.  Press five if this is a personal call.  Press nine if the call is of utmost urgency, to put yourself on the line immediately if I'm on the phone, or set off an alarm if I'm not.}''



I seriously debated pressing nine.  I \emph{felt} like this was a nine.



I hit one instead.



``\emph{This is James, receiving a call for Mr. Chambers.}''



``It's Weaver, I\ldots I don't know who else to call.''



I wasn't coherent, which was unusual, considering how I could normally keep myself together in a crisis.



``\emph{Oh, Weaver!  He's actually talking to someone about you right now.  I got his attention.  He'll be with you in a second.}''



``I'm not sure I have a second,'' I said.  There was no response.  He wasn't on the line.



``Oh man,'' Golem said.  ``I'm\ldots oh fuck.''



Quite possibly the only person who was as concerned as I was.



``\emph{Glenn here.  You should have called earlier}.''



``I didn't get a chance,'' I said.  I would have explained, but time was precious here.



``\emph{I imagine you didn't.  Well, there's good news and bad news.  You've already run into the bad news.  Here's the good.  This?  It's my plan they're using}.''



I could believe it.  I didn't respond.



``\emph{Their timing is off.  I would have done this differently if I were your enemy.  It's too much of a gamble as it stands.}''



``They planned this, have been setting it up for a while.  I expected interference with the missions, being supplanted with the Protectorate squad, not this.  I just need to know--''



There was a fanfare, musical, light and jazzy.  By the time it faded, a crowd I couldn't see had started applauding.



``It's starting,'' Tecton said.  He was a \emph{pillar} of confidence here.



Glenn was talking, but I couldn't hear over Tecton and the crowd.  I stepped away, my free hand raised to block out the noise.



``\emph{\ldots{}nds like the show just started.  They have to have leverage against you if they're pulling this.  Your probation?}''



``They're threatening to declare a breach if I don't play along.''



``\emph{Play along.  I heard what you did, announcing what the PRT was doing to the entire building.  Word got around, in certain channels.  Do not do that again.  Don't call your bosses out and let people know that you don't want to be here.  They'll be ready for it, and you'll hurt worse than they do.''}



``Okay,'' I said.



``\emph{Did they prep you?}''



``No.   I got off a six-hour graveyard patrol with Gauss and returned to the base to hear about this.  They even put our new Protectorate member on the comms to keep me out of the loop, then fed me \emph{just} enough information I had to listen without telling me \emph{enough}.  I've never even seen this show, and I barely had time to get my costume brushed off and my hair in order.  They tidied it up some here, but--''



Glenn cut me off.  ``\emph{Okay.  It's not the end of the world, but I don't think this show will help you.  These shows almost always result in a ratings dip over time}.  \emph{It boosts your appeal but hits you on respectability.  It's only worth it if there's}\emph{merchandise or media to sell, which there isn't.  They're tanking you.  Still, this is minor in the grand scheme of things.}''



Being in front of millions of people was minor.  It wasn't that I hadn't had appearances before, but most had been without my knowledge.  The unveiling of `Weaver' was a good example of how tongue-tied I was liable to get.



``What do I \emph{do}?  How do I approach this?''



``\emph{I'd tell you to just be yourself, but that's a terrible idea.  Be yourself as you normally are with the Wards.  Be the teenager, the friend.  Play up the fact that you're a group, that there's camaraderie.  Build a relationship with the audience by sharing things they probably don't know.  Nothing sensitive.}''



I wondered if the dildo prank that the Wards had initiated me with would qualify as sensitive.



More than that, I wondered if I even had enough of a bond with the others, something I could draw on.



``\emph{Be engaging.  It's more important to keep the conversation moving than it is to say what you want to say.}''



``Wards!''  A woman called out.  ``All together.  Hurry up now.  You're on in two minutes.''



Like a kindergarten teacher herding students around.



``Two minutes,'' I said.  ``I should go.''



``\emph{Good luck.  This is a day the strategist needs to take a vacation, understand?  Or delegate a task to it.  They're putting you out there because they think you'll either take a hit to your reputation or you'll try to be clever and self destruct.  You stand to lose more than they do, and this isn't live, meaning they can pull anything they don't want on the air.}''



``I get it,'' I said.  ``They aren't just giving me enough rope to hang myself with, they've put me in a rope factory.''



``\emph{Exactly.}''



``Thank you, Glenn.''



I joined the others, my heart was pounding with enough force that the thumps rocked my entire body.  Tecton was closest to the stage, followed by Grace and Wanton.  The core team members, the veterans.  Veterans in one sense.  Wanton didn't have half the field experience I did, even with our sustained campaign against the local villains, starting to help out in Detroit and trying to deal with that one jerkass in Milwaukee who we hadn't yet managed to pin down.  Tecton and Grace were a little more seasoned, but not by a lot.



The stage manager was checking the microphones everybody wore.  She paused by me, and ensured it was plugged in, and that the connection was unbroken.  I was essentially wearing the same costume I had in the winter, but had skipped the extra layer beneath.  I suddenly felt intensely conscious of every wrinkle and all of the grit that had gathered up around my ankles and feet as I'd patrolled.



The costumes the \emph{others} wore were immaculate.  Wanton had styled his hair to be messy in a good way, and was draped in flowing, dark blue clothing with lighter armor situated across his chest, his waist, his boots and along the length of his arms.  I suspected that the cloth afforded him more protection than the thin plates of metal, but it served to mask his artificial arm.



Grace's costume was light, in contrast to the dark of Wanton's.  Her new costume was white cloth, almost a martial artist's outfit, but designed to offer more coverage.  Reinforced pads were situated at every striking point, complete with studs to offer more traction and focused impacts.  There wasn't a single hair out of place beneath her combination headband, hairband and mask.  She had glossy, wavy locks I was a little jealous of, and a trace of lipstick.



I wish I'd considered some make up.  Not that I wore a lot, or that I'd had the time.  I had only what they'd given me in the studio, and they hadn't gone overboard, on the assumption that I'd keep my mask on.  No, if anything it forced me to keep it on.  Heavy eyeshadow to make it easier to see my eyes behind the blue lenses.



Cuff seemed to be in the same department as Grace.  She'd done herself up, with a more ornate braid to her hair, and had altered her costume a fraction, to allow for more decorative tailoring at the ends of each panel and the nose of her visor.  Slivers of skin were visible between some slats of armor at the upper arms and collarbone.  Of everyone here, she seemed the most excited.  She couldn't sit still, but she was smiling, and it was a genuine expression.



That left Annex and Golem.  Golem was uncomfortable, and I couldn't blame him.  Like me, he had details he'd want to hide.  His family, his background, the fact that he was in foster care.  His costume, too, was a work in progress.  It was a resource for him, and maximizing that resource often set him back in the appearance department.  Annex, by contrast, had settled into a `look'.  It was plain, intentionally so.  The white cloak was form-fitting, with ribs to keep the fabric straight and close to his body so it was easier and quicker to absorb.



``Grace,'' Tecton said.  ``No swearing.''



Wanton snickered a little.



Tecton pitched his voice lower.  ``Golem?  You've \emph{got} to stop calling adults sir while you're in costume.  You do it as a civilian, dead giveaway.  Hasn't mattered up until now, but this is the test.''



``I probably won't say much,'' Golem said.  ``I'm so nervous I feel like I need to puke.''



``No puking,'' Wanton said.



``No puking is a good idea,'' I agreed.



``Weaver\ldots'' Tecton said.  He gave me a look, with only his eyes visible behind his helmet.  ``\ldots{}I don't even know.  But I've kind of gone the extra mile for you, and you've done a lot in return, but--''



The stage manager stooped down a little to talk to us, even though both Tecton and I were both taller than her.  ``Alrighty, guys!  You're on in five, four\ldots''



``I still owe you one.  I'll be good,'' I told Tecton, just under my breath.



``One!''



The jazzy fanfare played.  As if that wasn't cue enough, the stage manager gave us a little prod, literally pushing Tecton forward.



It was surprising how small the studio was, both the stage with its slate gray floor and fake cityscape behind it and the studio audience.  Tecton led the way to the half-circle of a table with the three hosts on the far side.  The largest chair closest to the hosts was undoubtedly his, shipped here by the PRT so he could sit down in his armor without crashing to the floor.



We sat down.  Tecton, Grace, Wanton, me, Annex, Cuff and Golem, in that order.  The music died as we took our seats, opposite the three hosts.  An adult man, African-American by the looks of it, a woman with peroxide blond hair and a girl who could have been her daughter, a brunette who bordered on overweight, with a winning smile and an overly generous chest.



``Welcome back to \emph{Mornings with O, J and Koffi},'' the woman said.  ``School's out for the day and we've got the Chicago Wards here for breakfast.  Good morning, guys.''



We voiced our replies.  Wanton gave me a look, smiling, and I made myself smile as well.



The young girl gave a small wave, ``\emph{So} nice to meet you.  We had the team here before, but you guys have definitely changed things up since.  Campanile was the team leader then.''



``Campanile graduated to the Protectorate a little while ago,'' Tecton said.  ``He said to say hi.''



``You were there too, weren't you?'' Koffi, the man, said.



``In my old costume,'' Tecton said.  ``Which I'd prefer we didn't talk about.''



There were chuckles from the hosts at his comment, and the audience echoed them.  It was oddly surreal.  I intended no offense to Tecton in thinking it, but the comment just wasn't that amusing.



``The updated costumes look good,'' Koffi said.



``We can thank Weaver for that.  Any cloth you see is spider silk,'' Tecton said.



``Spider silk, wow!''  This from the blonde woman.



``Cuff and I sort of missed out on that front,'' Tecton added.



``I don't know whether to be amazed or freaked out,'' the younger woman said.



``We had a giant Japanese crab on the show just a month ago, I think.  Jo had to leave the stage,'' Koffi said.  ``I think she's a little nervous with Weaver here.''



``That was \emph{so} embarrassing,'' the young woman said.  I made a mental note of her being `Jo'.  ``And you're \emph{never} going to let me live it down.''



More laughter.



\emph{Oh hell}, I thought.  It was all so fake.  Fake responses, fake conversation.  The personalities, the way they were over-talking, it was like they'd taken everything that irritated me and condensed it into \emph{this, }and situated it all in front of countless viewers so I couldn't even respond the way I wanted to.



``I don't dislike \emph{you}, Weaver,'' Jo said.  ``It's \emph{bugs I don't like}.  I'm not nervous.''



``Thank you.  Good,'' I said.  Then, in an attempt to recover the clumsy sentence, I added, ``I'm glad.''



The blonde, who was `O' by the process of elimination, said, ``There's been a fair bit of attention directed at your team.  The leaked video thrust you all into the spotlight.  Then you dropped off the radar.''



``Recuperating,'' Tecton said.  ``We're teenagers.  We go to school and play video games and being a cape is only part of it.''



``Except for Weaver,'' Wanton said.



Both Tecton and I shot him a look, and then I remembered that there were eyes on me.  There was a reaction from the audience.  Light laughter.



``What do you mean?'' Jo asked.



How could I even explain that I was working towards stopping or mitigating the degree of the world ending, when I wasn't allowed to mention the fact?  Or that we were systematically targeting the most problematic villains, when I didn't want anyone to see the show and hear the battle plan outlined for them?



``Wanton has been poking fun at Weaver about how she doesn't go out or maintain any hobbies,'' Tecton explained.  ``Which isn't entirely fair.  My apologies to Weaver bringing this up, but it's not a secret that\emph{ }she's on house arrest.  She's on probation, and so she's limited in what she can do.''



Koffi seized on the topic.  ``You had a pretty colorful life as a villain, Weaver.  We've seen the cell phone video of you in the cafeteria of your high school, opposite Dragon and Defiant.''



I felt simultaneously glad that the conversation was \emph{moving} and horrified that I was the subject.  I blamed Wanton.



Still, I said, ``Clockblocker too.  I wasn't actually attending school, though.  It was a couple of unlucky circumstances that put me there, and\ldots yeah.  At that point in time, I'd wanted to focus on taking care of my part of the city.''



``That's \emph{interesting}, isn't it?'' O asked.  ``You were a criminal overlord.  How were you even qualified for that?''



``It wasn't like that,'' I said.  I was more nervous now, half-convinced I was damning myself further with every sentence.  I'd inevitably come off too harsh and `dark' for the civilians who were watching and too soft for any villains who happened to see.  Damn it.  ``Taking the territory and being a villain were independent things.  Related, but different.  It was after Leviathan attacked, food, water, shelter and safety were hard to come by.  It was a way to help.  If I'd been a solo hero then, I'd have done much the same thing.  I'd have been gentler, but yeah.''



\emph{With less money to spend}, I thought.  I'd avoided mentioning I was an undercover, aspiring hero when I'd started out.  That had \emph{never} worked out for me, and only complicated things.



``And Alexandria?  I think everyone's curious about your thoughts there.  You were shocked, in the video, when she made a reappearance.''



I shook my head.  ``It's not her.  I'm\ldots I'm not \emph{happy}, obviously, to see her up there.  It's an ugly reminder of what happened.  But to have another person fighting Endbringers?  I'm okay with that part of it.''



``A long, bumpy road, and it's brought you here,'' O said.



``With the Chicago Wards,'' I said\emph{, }in a vain hope to turn the conversation away from me.



She took my cue.  ``New costumes, a new group.  Behemoth is defeated and it looks like the Endbringers might have reverted to the schedule they had pre-2002.  An attack every four to five months.''



``Yes,'' Tecton said.  ``Everything's new.  There're a lot of changes going on.''



``Are you \emph{excited}?'' Jo asked.



Oh man, was I ever starting to dislike her.



``I'm \emph{really} excited,'' Tecton said.



The response caught me off guard.  Was he lying for the sake of appearances or was it honest?  How could someone be excited when the end of the world was nigh?  Did he not believe it was coming?



Whatever the answer was, I felt oddly disappointed in him.



Cuff shifted in her seat, and metal scraped against the metal of the chair's footrest with a high-pitched noise.  She whispered, ``\emph{Sorry.}''



O leaned forward.  ``It's fine.  Let's hear from some of the others.  Wanton, your thoughts?  Are the changes \emph{good}?''



``The changes are good.  I give Weaver a hard time, but she really kept us alive.''



``She did, by the looks of what happened in that video,'' O said.



Bringing the conversation back to me.  Again.



``Grace?'' she asked.  ``Thoughts on your team member?''



``If you told me way back on the first time we met that I'd come to respect her, I'd have been surprised.''



Jo looked at me.  ``Does that bother you?''



``No.  I respected and liked the Chicago Wards right off the bat, but I don't blame them if there was any suspicion,'' I said.



``Pretty generous.''



``If anything, I was pretty amazed by how they all pulled together in New Delhi.  Three of them were new, two hadn't even been in a real fight before, and they went up against \emph{Behemoth}?''



Cuff was perched on the edge of her seat, doing her best not to move and make things squeak again.  She had the ability to liquefy the metal touching her skin, which would have eliminated the problem, but the act would have ruined the look of it.  Part of that stiffness was anticipation, like a child who hadn't done their homework, sitting at their desk and dreading the moment where the teacher called on them.  A stark contrast to her excitement earlier.  Had the screech knocked her off cloud nine?



``Cuff,'' Koffi said.  ``What do you think?  We saw the video, and you were pretty scared at the start, there.''



``Terrified.''



``You got injured?  We didn't get to hear how.''



``A burn,'' Cuff said, smiling a little.  ``I recuperated in a few days.''



A lie.  She still hadn't fully recuperated today, eight months after the fact.  She might never.



``I \emph{love} to ask this question,'' Jo said.  ``What's it \emph{like}, being a superhero?''



She \emph{loved} that question?



``It feels weird to think of myself as a hero,'' Cuff said.  ``I'm\ldots I don't think I'll ever be one of the big heroes.  I'm not a cape at \emph{heart.}  Fighting isn't in my personality, and I got powers like this.''



``Cuff is a girly-girl,'' Wanton commented.  ``Her bunk at the Wards headquarters has pink sheets and rainbows and there's a unicorn picture on the--''



Cuff leaned around me to mock-punch him.  ``I'm not that bad!''



``You're bad, though.''



Tecton raised a hand to cover Wanton's mouth.  ``I'm thrilled to have her on the team.  She hasn't disappointed me yet.''



Cuff smiled at him.  ``\emph{Thank you.}''



I wasn't sure I'd have been able to say the same about Cuff, but my standards might have been higher.  She'd always done the job, but there was a reticence to her that wasn't going away.  Three months ago, in our first real conflict outside of fighting Behemoth, she'd needed a push to carry out an offensive.  Four days ago, in Milwaukee, she'd needed that same coaxing.



Cuff was competent.  She had her strengths, and was stellar in some narrow cases.  At the same time, I still worried if a moment's hesitation on her part would get one of us hurt somewhere down the road.



She was talking, happy to be in the limelight, stage fright forgotten.  ``I was saying what it's like being a hero.  It's overwhelming.  It's something that eats into every part of your life even if you want to limit it to four hours a day, four times a week.  If you don't train and exercise then you fall behind.  If you don't read the briefings on the bad guys, then you look stupid when you do run into them and have to ask someone.''



``I certainly hope you're not getting into serious fights,'' Koffi said.



``Um,'' Cuff said.  \emph{Stage fright back in full force}.  She'd touched on something that would get her a slap on the hand from the PRT, and now she didn't have her footing.



I was trying to think of a way to rescue her when Tecton said, ``Fights happen.  We're actively trying to avoid direct confrontation, but we patrol and we practice our abilities so we can handle ourselves in the real crisis situations.  Many of our members patrol with other capes so they can get experience while having someone to rely on in case of an emergency.''



All true, but he was omitting the fact that we were actively seeking out \emph{indirect} confrontation.  It was an admirable spot of double-speak, simultaneously reinforcing the atmosphere we were hoping to establish.  \emph{Heroes are} safe.  \emph{Everything is under control.}



``I kind of like those times,'' Annex said.  ``You get to hang out with the local powerhouses, hear what they have to say, learn from them.  I had a brief stay in a few other teams, but the one thing I really like about Chicago is that everyone is okay with me asking questions, and I have a lot.''



``Who's your favorite cape to hang out with?'' Jo asked.



``Shuffle.  Our powers work well together, if we're careful not to let them interfere.''



``And Golem?  I can almost guess.  When Campanile appeared in the evening news, he had some promising words to say about the Protectorate's newest member.  When we asked him who the most promising new recruit in the Wards was, he named \emph{you}.''



``Ah,'' Golem said.  ``Yeah.''



``Do you think you can live up to that?''



``I \emph{hope} I can,'' Golem said.



The conversation was faltering.  I thought of what Glenn had said.  Showing some of the bonds between team members.  If I had one with anyone, it was with Golem.  The running, the shared perspective on the end of the world, the fact that we were both Brockton Bay natives\ldots



``Everything Tecton has been saying about Cuff is true for Golem,'' I said.  ``If he's getting praise from the heroes, he deserves it.  He's a classic hero at heart.''



``A classic hero?'' Koffi asked.



``He's like Tecton.  Grace and Annex are too, to a lesser degree.  He's genuinely good-natured and kind.  When everything starts falling apart, he's still there, naturally courageous.''



``I like how I'm omitted from that list,'' Wanton said.  ``Only person who hasn't been praised so far.''



``\emph{I} think you're awesome,'' Jo said, smiling.  The audience cooed.



``Golem's \emph{steadfast},'' I said.  ``He's working out, he's studying hard for both regular school and cape stuff.  And with all of that going on, he's still generous enough to help me out with my stuff.  Like Tecton said, I'm limited in where I can go and when, and Golem helps with that.''



The running, primarily, but not wholly that.  He'd walked with me to the mall once or twice.  I didn't want to share details, though, in case people decided to try to find us while we were out, with Golem not in costume.



``Do relationships develop in this environment?'' O asked.  ``Anything besides friendship?''



``If you're talking about Weaver and me, then no,'' Golem said.  ``We're friends.''



``Friends,'' I asserted.



``You had a thing going on with Grue,'' Wanton chimed in.



``And this is the \emph{third} time you've turned the conversation awkwardly back to me,'' I retorted.



He gave me a sheepish grin.



``A tender moment on the battlefield,'' O said.  ``I think a lot of people were surprised.''



\emph{It was a personal moment}, I thought.  If I harbored any ill will towards Glenn, it was for that.  He'd deleted sound or video where it gave up identifying details, like the nature of Cuff's injury.  He \emph{hadn't} erased the scene with the woman in the suit, but the reception hadn't held up that deep underground, so there was no need.  He'd also been kind enough to erase the scene where Imp had promised to get revenge on Heartbreaker.  The villain hadn't been notified of her plan.



But all of the bonding, the closeness, leaving interactions with Rachel open for hundreds of millions of people to speculate on?  That was scummy.



Necessary on a level, but still scummy.



I hadn't replied to his statement.  I almost wanted to let the silence linger awkwardly, just to nettle them and drive home that it wasn't their business.



Jo didn't give me the chance.  ``You talked about Tecton and Golem as naturally heroic people.  What about you?''



Man, her questions irritated me.  Asking questions where they already knew the answer or where the answer was so immaterial\ldots  Who watched this kind of garbage?



Why was I being forced to support it by my presence?



``I was a villain for three months,'' I said.  ``Maybe I'd like to think I was a little bit heroic as a villain, and I'm a little bit villainous as a hero.  But I'm working on that last part.''



``Hold on, hold on.  You think you were \emph{heroic, }before you switched sides?'' Koffi asked.  ``By all accounts, you killed Alexandria and a law enforcement official.  You were quoted as talking to schoolchildren about the huge quantities of money you earned from criminal activities.''



Was he just sitting back, \emph{waiting} for an opening?



Grace stepped up to my defense.  ``She said a \emph{little}.  She fought the Slaughterhouse Nine.  She helped the people in her district.''



``That actually sounds impressive,'' Jo said.  ``If that's a little, then I wonder what being a little bit of a villain nowadays is like.''



She tittered along with the audience's reaction.



``No response?'' Koffi asked.



They were ganging up on me.  I wished I knew who these guys were, what their normal style was, so I could roll with it.



``I'll let my actions speak for themselves,'' I said.



Tecton was quick to speak, backing me up.  ``I think that's the best way to go about it.  It's untreaded ground, in a way, to have a notorious ex-villain on the team.  Whatever happens, people are going to wonder where she stands, if \emph{I've} been corrupted by association, or if this is all some elaborate scheme.  But we can work on it.  She can keep doing good work, and hopefully a few months or years down the road, I'll still be able to say that Weaver's a good person at heart and she's done a lot for the good of the city and the world, you know?  Some people won't be convinced no matter what she does, but time and reliability should let Weaver prove her worth.''



``Makes sense,'' O said.  ``We're rapidly approaching another ad break.  I don't suppose we could get any of you to step up to the plate?  A demonstration of powers?  A neat trick?''



I almost volunteered, but then decided against it.  I didn't want to spend \emph{more} time in the spotlight.



Annex stood from his chair.



``One of the new members!  Excellent!''  Jo said.  ``We've got a crash test dummy, a beat up car\ldots''



``I can do something with the car.  Maybe we could remodel the exterior?'' Annex asked.  ``Maybe the audience could name a car?  What should we make?''



Jo hopped out of her seat, arm raised like a kid in class.  She was short.  I mentally re-evaluated my estimation of her age to put her closer to her late teens than her early twenties.



A series of beeps, not even a half-second apart, interrupted all of us.  Our phones?



I was still drawing my cell from my belt when I saw a commotion backstage.  People who'd been standing still were running now, talking into headphones.



My cell phone screen was surrounded by a thick yellow border.  A text was displayed in the middle.



Stand by.



Disturbance recorded.



Possible Class S threat.



The others had identical messages on their screens.



There were murmurs among the audience members as someone from backstage stepped up to talk to Koffi and O.



``It can't be,'' Cuff said, her voice quiet.



``We got texts just like this for the incident where we met Weaver,'' Tecton said.  ``It could be a similar situation.''



The lighting changed.  Tecton stood from his seat, and I joined the others in following suit.



A studio employee advanced to the front of the stage.  When he spoke, the microphone headset he wore carried the sound, ``A possible emergency has come up elsewhere in the world.  If this blows over in the next few minutes, we'll edit out anything problematic and resume the show.  For now, remain calm while we prepare for an emergency broadcast from the news team upstairs.  There is no danger here.''



My phone buzzed.  I checked it to see another text.



Chicago Wards are to remain at current location.



Transportation en route.  Will deploy to studio B parking lot for quick pickup.



A little more ominous than the `maybe' the studio employee had given us.



Panel by panel, the backdrop of the `Mornings with O, J and Koffi' set transformed, images flickering to show a composite of a grainy, long-distance shot of a city.  It had been taken with a cell phone, and the resolution didn't translate well with the size of the `screen'.  There were tall buildings, neon signs glowing in the late evening.  Somewhere in Asia.



``Japan,'' Wanton said.



The camera was shaking, and the view on the screen reacted in kind.



Dust rose in clouds, billowing, until they obscured the camera's view.



The audience was reacting.  Moans, cries of alarm and despair.  They knew what was going on.



``Please be the Simurgh,'' Cuff said, her voice small.  Grace put an arm around Cuff's shoulders.



\emph{That may be the first time in history anyone's thought that}.



\emph{She's right,} too.\emph{  Even the Simurgh would be better than this}.



The timing, the fact that it was happening so soon after Behemoth had died\ldots it was all wrong.



Behemoth had come from deep underground.  Leviathan had emerged from the ocean.  The Simurgh had approached from the far side of the moon and descended to hover just above the tallest building in Lausanne.



The fourth, it seemed, was appearing in plain sight.



The dust took forever to clear.  But for a few mutters here and there, small animal sounds of despair from the audience and studio employees who were watching, the studio had plunged into quiet horror.



It stood somewhere between Leviathan and Behemoth in height, if I ballparked by the number of stories in the adjacent buildings.  I waited patiently for the view to clear, revealing more details.  Clues, as if there was a solution to what we faced here.



I pegged him as a he before I saw too much else.  He was broad, a Buddha in physique, if more feral in appearance.  He was as black as night, with something white or silver giving definition around the edges of his various features.  He didn't wear clothes, but he had features somewhere between leaves and fins, with elaborate designs at the edges, curling away from elbows, his wrist, his fingers and around his legs. It made his fingers and toes into claws, and left dangerous looking blades elsewhere.  His face was a permanent snarl, frozen in place, his teeth silvery white behind the ebon lips.  Tendrils like the whiskers of a catfish marked the corners of his mouth.



All across the exterior of his body, there were gaps, like the gills of a fish, and that brilliant white or silver glimmered from beneath, a stark contrast to the absolute black that marked the rest of him.  It made me think of a tiger.  And at the center of it all, quite literally, there was a perfect sphere of that same material, a marble or a crystal ball, his body perched on the upper half and his legs attached to the lower half.



Arms extended out to either side, he took a step, almost \emph{waddled}.  He floated as though he were walking on the moon.



``He's not a fighter,'' I murmured.



``No,'' Tecton agreed.



``What \emph{is} he?'' Grace asked.



People were fleeing, still in close proximity to the site, evacuating tall buildings.  The Endbringer stopped and extended a hand.  His arms weren't long enough to reach around his girth, but his upper body rotated on the sphere that formed his midsection, giving him the freedom of movement needed.



The camera shook as he used his power, and an unseen cameraman had to catch it before it fell.  A faint glowing line appeared on the ground, a perfect circle.   The light gradually intensified, reaching higher, and the space within the circle seemed to darken in equal measure.



It moved, the circle roaming, the glowing lines adjusting to scale obstacles and account for higher ground and dips in the terrain.



When it intersected a building, the effect became clear.  Barely visible with the camera's range, they were nonetheless a blur, moving within the circle's perimeter.



``They're trapped,'' Golem said.  ``He's manipulating time in there and they're trapped.''



Golem was right.  How many days were they experiencing in there, with only the food they had on hand?  Was water reaching them?  There didn't seem to be power.



``Oh god,'' Cuff said.  ``Why isn't anyone stopping him?''



``There's no heroes on scene,'' Tecton said.  ``Japan doesn't have many dedicated heroes anymore.''



It took six or seven seconds for the blurring of their movements to slow.  In another second, it stopped altogether.



He left his power where it was.  The glass on the building's exterior cracked.  Cracks ran along and through the other material, in the street and at the edges of the structure.  It leaned, then toppled, and the destruction was contained inside the effect.



Wanton spoke, almost hesitant.  ``Is that- doesn't that remind anyone of--''



``Yes,'' Grace said.  ``The barrier, the time manipulation.  It's similar.''



\emph{Similar to what we did.}



All in all, the Endbringer was there for a minute.  The effect moved on, and it left a ruined husk of a building behind.  Though there was no sun shining, the stone and terrain had been sun bleached, worn by elements, eroded.



The Endbringer extended his hands out to either side, and two more glowing circles appeared.  Like the first circle had, they flared with light.  Like the first, they moved, drifting counterclockwise around him.  It was a slow, lazy rotation, slower than a moving car but faster than someone could hope to run.



He advanced with floating steps, and the circles maintained a perfect, steady distance away from him and from each other, orbiting him like the shadows cast by three invisible moons.  Here and there, people and cars were caught inside.  He wasn't a full city block down the street before one circle had a crowd trapped within, half-filling the base of it, another circle perhaps a quarter of the way full.



He moved through a less populated area, and he left trails of skeletons in his wake, in odd fractal patterns that followed the circles' movements.



He chose what entered and he chose what left.  An attack form that couldn't be defended against, only avoided.



``Movers will be important,'' I said.  ``Maybe shakers too, if we can find a way to stop him or his circles from progressing.  His threat level depends on how fast and how much he can move those time-stop areas.''



There was no reply from the others.



I glanced at Cuff, and I saw that she was hugging Grace.  She was silent, but tears were running down her face.  Grace was more resolute, but her eyes were wet.



The timing, it was wrong.



Strategy, figuring out a battle plan, it was crucial here.  The first attacks were often some of the worst for cape casualties, if not necessarily the overall damage done.  Too many lives would be lost in finding out his general capabilities.



But it didn't matter.



I reached out and took Cuff's hand, holding it.  A glance in the other direction showed me Golem.  I took his hand too.



This was the key thing in this moment.  Not the future, what came next.  Support, morale and being a team in the \emph{now}.



Silent, we watched as the heroes engaged.  Eidolon and Legend joined the Japanese heroes in fighting the unnamed Endbringer, keeping a safe distance.



One circle disappeared, and the Endbringer reached out.  Defending capes were too slow to escape the perimeter before the effect took hold, a new third circle forming.  Eidolon tried hitting the effect with three different powers, but it didn't break.



``\emph{No, no, no\ldots}'' Cuff whispered.



In a minute, the capes were dead.



Our phones beeped, and I felt a moment's despair.  We'd have to fight this thing.



Ship is outside if you want it, Chicago Wards.  Attendence \underline{not} mandatory.



Temp. codename is Khonsu.



``I'm\ldots'' Cuff said, staring down at the phone.  ``I'm staying.''



``Okay,'' I said.



``You're going?'' she asked.



I nodded.



She nodded back, swallowed hard, before she turned her eyes back to the screen.  In that moment, the Endbringer, Khonsu, reversed the direction the circles were drifting, extending the distance they were orbiting around him in the same movement.



Capes who'd been trying to time their advance to close the distance to Khonsu were caught.  Four trapped and doomed to die a slow death, a fifth caught between a building and the orb's perimeter as the circle continued its rotation.  When the circle had left the building behind, there was only a bloody smear where the fifth cape had been.  Skeletons for the rest.



Now he stood still, weathering attacks with the same durability the other Endbringers had.  Damage to his flesh exposed silver, and damage to the belly or other silver parts showed ebon black.  The onionlike layers Tattletale had described, plain to see.



I tore my eyes from the screen, marching towards the emergency doors.



So much was wrong with this.



It wasn't fair, it wasn't right.  Fucked on so many levels.



A woman was sobbing in the hallway as we passed.  A group of twenty-somethings in dress shirts sprinted down the hallway, carrying bags.



The dragon-craft was waiting for us outside, ramp doors open.



Odd, to see the sky so bright, when the battlefield was shrouded in night.



We stepped inside, entering the center of the craft.  I found a seat by a monitor, with a laptop ready and waiting for use, login screen displayed.  The monitor was showing the battlefield, roving over the dead, the buildings that had collapsed under the weight of years.  Oddly, the cameraman wasn't focusing on Khonsu or the defending heroes.  A few heroes were fleeing, but most weren't in view.



``We're ready,'' Tecton called out.  ``Ship?''



The craft hadn't taken off.



My growing sense of dread was confirmed as the image on the monitors changed.



\emph{Even with those circles being as devastating as they are, it wasn't enough.  There wasn't the same broad scale, the promise of lingering devastation}.



No.  There was something more to Khonsu.



The monitors showed him in a different city.  A caption on the bottom of the screen showed the words `Cape Verde'.



He'd teleported halfway around the planet.



All of the problems with getting to Endbringer fights on time, with mobilizing and dealing with the fact that half of our best teleporters and movers had been slain in past battles\ldots he was capitalizing on that weakness.



My phone vibrated to alert me to a new text.  I didn't need to read it to guess what it said.  I read it anyways.



Stand by.



``No,'' I whispered to myself.



The heroes were engaging, now.  Legend and Eidolon had caught up.  Khonsu had situated himself near some kind of military installation, and they'd wasted no time in readying for a fight.  Missiles and shells exploded around him.  The columns of frozen time that rotated around him caught many, and they exploded within the delineated structures.



For long minutes, he fought.  I watched, my eyes fixed on the screen, to see his behavior, to look for the cue.



He waded into and through the arranged military squadrons with their parahuman supplementary forces.  He was as tough as Behemoth or Leviathan.  No attack delivered more than scratches or nicks.



Five minutes, six, as he leisurely tore through the forces he'd caught off guard.  Eidolon ducked between two of the pillars of altered time and delivered a punch that sent the Endbringer tumbling.  The orbiting columns were pulled behind Khonsu as he moved, and Eidolon came only a hair from being caught.



Alexandria and other capes joined the attack.  Too few.  Everyone else retreated.



Khonsu didn't pursue.  He remained where he was, arms extended out to either side, palms down.



Then he disappeared in a massive, tightly contained explosion.  Trucks and sections of fence were thrown into the air by the movement.



Long seconds passed.  Then my phone vibrated.  Another text.



Cannot deploy until we have a way to pin him down.



Stand by until further notice.



I struck the laptop that sat in front of me.  One hinge holding it in place snapped.  I shoved it hard, and it fell to the floor of the craft.



``Fuck!'' I shouted.  ``Fuck it!''



I kicked the fallen laptop, and it went skidding across the floor, down the ramp and into the parking lot.  My foot stung with the impacts.



The other Wards were gathered, sitting or standing around the craft that was taking us nowhere.  There was no way to approach if he'd teleport by the time we arrived.  We'd never catch up to him.  The others were as quiet and still as I'd been violent, haunted, scared.



Nobody talked.  Nobody volunteered ideas, because we didn't have any.



I wasn't sure any of us knew how to fight this one.  Nobody in the Chicago Wards did.  Nobody elsewhere.  Speaking, commenting on the situation, it would only remind us of what we were facing.



Above all else, I wasn't sure I wanted to think about the detail we hadn't spoken aloud.  The thing, above everything else, that made this so fucked up.  In the nine years that we'd been fighting Behemoth, Leviathan and Simurgh, they'd never attacked this close together.



Even if we found a way to beat this \emph{Khonsu, }to mount a defense and stop him from picking us apart, settlement by settlement, darker possibilities loomed.



Two attacks, two months apart.  Had their schedule changed?  Would the next attack come in a mere two months, or would it be more unpredictable than that?



\emph{No}, I thought, with a dawning horror.  No, it was worse than that.  The Endbringer's schedule of attack had always depended on the number of Endbringers in the rotation.



If they were keeping to their usual rules, it promised a \emph{fifth}, waiting in the wings.





