





Three days.



Nearly three days and we hadn't managed to kill him.



A new target every thirty minutes, give or take.  Ten to twenty minutes for the defending forces to get their shit together.  The remainder of that time was our capes trying to hurt him.  Chipping away at him.



Sometimes we made headway.



Sometimes he crushed the bulk of the defending forces and then stood still, drawing those rotating columns of altered time to himself.  Not \emph{covering} himself, but allowing the altered time effects to graze the outer edges of his body.  He'd heal, regenerating as much as half of the damage we'd done.



He hit major cities and small ones.  Villages, even, when he needed some elbow room to regenerate.  He'd hit a weapons stockpile in Russia, and nuclear weapons had been accelerated in time, the casings wearing down in that odd entropic, eroding effect that accompanied the time accelerations.  A nuclear detonation.  Heroes were still trying to minimize the damage.



He was teleporting less often than he had at first, and there were a number of heroes who were appearing regularly on the scene.  Legend, Alexandria, Eidolon, they were stepping up, though they'd started taking breaks, \emph{shifts}.  Legend would skip one, then participate in the next two.  Alexandria would do two on, then two off.



They were tired, weary.  Everyone was.  How could you rest when he could appear where you were?  Six or eight hours of sleep meant he'd be changing location twelve to sixteen times, if not more.  And at the same time, that fatigue, it made it easier to make mistakes, and he wasn't an opponent that let mistakes slide.



Tecton approached me, setting his hands on my shoulders.



``What?'' I asked.



``You need to rest.  The others have managed it.''



``I've napped.''



``\emph{Sleep}.  You're swaying on your feet.''



I wanted to protest.  My eyes fell on the others, and I could see how affected they were.  Scared, tired, helpless.  They were arranged around the Chicago headquarters, perpetually in costume, with no idea what to do with themselves.  Thirty minutes, and then that intense period of tension, waiting, wondering as it took the media or the PRT time to grasp just where he'd gone, to report the information.  If we were lucky, we got video footage, and we didn't have to wonder if Khonsu had caught any of the big guns.



In a way, I'd grown used to being a little different from my peers, here.  I could be blas\'{e} about things that had them freaking out, confident.  I could put myself in the bad guy's shoes because I'd been one, once.



Except here, I was no different.  Three days in, unable to sleep for more than an hour or two at a time, feeling my heart plummet into my stomach every time Khonsu teleported, I was on the same page as the others.



``I only ever wanted to do something to help,'' I said.



``I know,'' Tecton said.



``Even at the beginning, even when I was undercover in the Undersiders, I wanted to stop the bad guys.  A lot of it was selfish, me wanting to escape, but I still wanted to work for the greater good.''



``Yeah,'' Tecton said.  He let his gauntlets fall from my shoulders.  I turned around to look at him.  Our man of iron, his face hidden beneath his helmet.  He was standing firm, giving no indication of how affected he was.  It let him be strong, or \emph{appear} to be strong, for our sakes.



``And then I decided to be a villain full-time, but my motivations were still sort of \emph{good}, even if I wasn't.  I knew the Undersiders needed help.  That there was something wrong with a lot of them, something missing in them.  And being a part of all of that, it was a way to help Coil, when I thought his plan was something \emph{good}.''



``You're not a bad person, Taylor.''



``I'm not\ldots being \emph{good} or \emph{bad} was never a thing for me.  Not really.  It was all about the actions I was taking and \emph{why}, instead.  I became a warlord and I took care of people.  I helped seize the city from Coil and we started implementing changes.  Again and again, I've escalated in terms of the kind of power I wield.''



``Do you think you're more powerful now?  With the Wards?''  He sounded almost surprised.



``I\ldots think so.  Yeah.  Maybe my hands are tied, I can't be as direct or ruthless as I would otherwise be, but I can reach out to the villains and I can reach out to the heroes, and I can affect a kind of change.  I have resources.  Tools and information I might not otherwise have.''



``Makes sense,'' he said, his voice soft.  ``Taylor, you need to sleep.  I can hear it in your voice.''



``I just\ldots why is it that I get more powerful over time, and yet I feel more and more helpless?''



``You ask too much of yourself,'' Tecton said.  ``You could have all of the power in the world, and you'd still feel like you should do more.''



``If he hits Brockton Bay--''



``Your father and friends will be okay.  Hell, our strike squad that we used against Behemoth was made up of Brockton Bay residents, wasn't it?''



``If I have to watch people I care about getting hurt while I'm helpless to do anything, I'll lose it.''



``It wouldn't be constructive to lose it,'' Tecton said.  ``And you're more likely to lose it if you're tired.  Go sleep.''



I didn't reply.  Instead, I trudged off to the quarters that had been set aside for me.  Roughly pie-shaped, with the door at the tip, it sat at the edge of the `hub'.  I had a bedroom upstairs, more personal, more of a home, but I didn't want to be that far away.  I didn't want to lapse into being Taylor Hebert, even in a moment of rest.  Better to keep thinking, keep considering options.



I lay down on the bed, pulling my mask off.  I didn't put my glasses on.  My vision was blurry, but it didn't do anything to block out all of the individual little lights, some blinking, that studded the interior of my quarters.  Laptops, batteries, alarm clock, the charging station with my spare flight pack inside, the television screen, the slat of light that filtered in beneath the door\ldots so many little points of light.  If I hadn't been so tired, I might have blocked the lights.  Using bugs wouldn't work, as they'd wander, but a towel at the base of the door, books propped up against various devices\ldots



I sighed and draped my arm over my eyes, my nose in the crook of my elbow.



I spent a long span of time in the twilight of near-sleep, trying not to listen to the murmurs of people's voices in the main hub.  Idly, I wondered how much time was passing.  Where was Khonsu attacking now?



A lot of people crossed my mind, too.  Enemies, allies.  How were they dealing?  My dad had fired off emails, asked that I let him know before I joined the fight, and right after I got away safely.



For every cogent thought that crossed my mind, two or three stray thoughts followed.  The devastation, scenes burned into my mind's eye.  People caught and left to die of dehydration in Khonsu's fields.



Somewhere in the midst of that, I managed to drift off, the recollections becoming dreams, or something close enough to feel like it was an immediate transition.



My uneasy rest was interrupted by a touch to my shoulder.



My eyes opened, and I could see the vague shape of a woman standing over me.



\emph{Mom}?



I was awake and alert in an instant, but she was already turning away.  Not my mom.  Dark haired, but too short.  Both of my parents were taller than her.



I only recognized her when I saw the doorway.  A rectangle of light, almost glaringly bright, just beside my closet.



``Hey,'' I said, as I hopped up from my bed.



She didn't respond.  She was already gone.



But the doorway remained open.



I had to cross the length of my quarters to see the interior.  A dark hallway, with only dim lighting cast by tubes recessed into the ceiling.  The woman in the suit wasn't on the other side.



I accessed the various storage containers for the bugs I was keeping in the workshop upstairs.  Beetles navigated the trap that kept them from flying out, then made contact with various touch panels, opening the cages where the various individual species were kept.



As a mass, they flowed down the stairs and into the hub.  The Wards who were at the command center and watching the monitor stood, alarmed, as the mass of bugs made their way across the room to my quarters.



``Taylor.''  It was Tecton speaking, hurrying to the door of my room.



The bugs filtered into my quarters through the space where the walls joined, and beneath the door.



My swarm entered the hallway.  No traps.  The woman in the suit was standing off to one side.  I stood at the threshold, and glanced down at the tracking device that was strapped to my ankle.  What the hell would happen if I stepped through?



I supposed I'd find out.  I stepped through in the same moment Tecton opened the door.



The rectangular portal closed, and I was left staring at a wall.  I turned to see the woman in the suit.  She was tidy, her hair tied back in a loose ponytail with strands tracing the side of her face, and she held a fedora in one hand.  The hat was beaded with moisture.  Another excursion she'd made before reaching out to me?



I was going to speak, when I noticed another presence.  A non-presence.  It was a shift of air currents that seemed unprovoked, affecting certain bugs when it should have touched other bugs in front or behind them.



The topographical sense I got from the movements of my bugs suggested a woman's form, nude.  It wasn't entirely gone when another appeared across the room.  The way they moved in sync- not two people.  One person, if she could be called a person; a phantom, flowing through the space around me and the woman in the suit.



The woman in the suit extended the hand that didn't hold her hat, directing me to a doorway.



I glanced at the woman, noting how there wasn't a trace of the anxiety or exhaustion that everyone else seemed to show.  My swarm checked the path.



There were people I recognized on the other side.  I stepped through.



The area was dark, but there was ambient light from a series of panels.  Large panels, floor to ceiling, eighteen by five feet, had been erected in a general circle. Two accompanying panels, only two or three feet wide, were set up on either side of each larger panel, to cast light at a slightly different angle.  A bar sat at just below waist height, a semicircle, simultaneously a handrest and a way of indicating a boundary the designated parties weren't to cross.



A different person or group of people at each station, lit from behind rather than the front.  The light from the other stations barely reached them, which meant their features weren't well illuminated.  Distinct silhouettes, with only a few more reflective materials catching the light.



I ventured up to the panel closest to the door I'd entered.  Tattletale stood there, and I deigned to stand just behind her and to her left.  Grue, I saw, was leaning against the panel itself, his arms folded.  Tattletale glanced at me and smiled, and I could just barely make out the white of her teeth.



``Asked if they'd pick you up,'' she murmured.



``Thank you,'' I said.  ``What is this?''



``Isn't it obvious?'' she asked.



She turned her attention forward, and then she was taking it in.  I didn't want to interrupt her, with the amount of information she was doubtlessly gathering.  It \emph{was }obvious, considering the general presence of those who'd gathered, even if I could only recognize a handful.



Opposite us, Chevalier's silhouette was unmistakable.  His cannonblade was too distinct.  Exalt stood to his left, and a cape I didn't recognize stood to the right.  I wondered momentarily if it would count against me that I was standing here.  It hadn't been by choice, exactly, but it wouldn't look good that I was with the Undersiders.



Bugs helped me make out Dragon and Defiant at the station to Chevalier's left.  Both wore their power armor, but apparently the presence of firepower wasn't a concern, here.



For the most part, that was where my ability to recognize people stopped.



To my left, there was a man in power armor with his face bared.  The tattoo across his face reflected a dark blue-green in an odd way, as though he stood beneath a blacklight, flecks of light\ldots only the fragments \emph{flowed}.  No, they were traveling a circuit, instead.  Faintly blue, the glimmers traveled a circuit that marked the interior of an elaborate, stylized cross, his eyes unlit shadows in the midst of the two horizontal bars.



I could make out a station with a woman, black, accompanied by a massive shadow of a monster with an auroch's skull for a head.  The woman's head hung, her hair braided or bound into dreads, I couldn't be sure.  I moved my bugs closer to check to see if she had any weapons, and her pet shadow reached out to block the swarm.  They died so quickly it was almost as though the shadow had killed \emph{before} it made contact.



I decided to leave her alone.



Further down, hard to make out due to the angle of the panel that framed them, there was a small crowd.  A young girl stood at the forefront, and others were gathered around and behind her.  My bugs noted twelve people gathered in front of the panel.



Another station had only a woman and a man sitting at a table that had been set out.  The man had his hands folded neatly in front of him, and the light from neighboring panels was reflected on the large-frame glasses he wore. The woman leaned forward, elbows on the desk, hands clasped in front of her mouth.  Dark skinned, with some kind of pin in her hair.  My bugs traced their hips – the area least likely to be unclothed, and I noted the presence of ordinary clothing.  A button up shirt for him, a knee-length skirt and blouse with accompanying lab coat for her.



Three men in robes that bore a striking resemblance to Phir S\textoverline{e}'s were arranged to our right.



``One moment longer,'' the woman in the lab coat said.



``Quite alright,'' a man answered her, from the group of twelve.  ``I'm really quite excited.  Been a rather long time since I've had a breath of fresh air.''



``\emph{Hush, Marquis},'' the girl at the front of that particular group spoke, and her voice was a chorus, a number of people speaking in sync, ``\emph{I will not have you speaking out of turn.  Our hosts have been gracious to invite us, you will not offend them and besmirch my reputation by association.}''



``My sincere apologies.''



\emph{Marquis?}  I had to search for the name for a moment.  Then I stopped.  \emph{That} Marquis?



Another panel lit up, and the circle was complete.  My bugs found the people gathered in front, allowing me to investigate that crowd, who had silhouettes I couldn't make out in the jumble.  A woman with a ponytail and a number of monstrous parahumans behind her\ldots  Faultline.



The woman in the suit arrived in the room, crossing through the darkness at the center with the steady taps of her shoe heels against the hard floor.



She joined the man with the glasses and dress shirt and the woman with the lab coat.  It clicked for me.



\emph{Cauldron}.  I was looking at the people behind Cauldron.  I felt a chill, despite myself.



``Ms. Alcott declined to join us,'' the woman in the lab coat said.  ``As did Adalid, who wanted to be ready to defend his home in case the new Endbringer arrived there.  The three blasphemies and Jack Slash were unreachable, but we would have far fewer problems if individuals like them could be reached so easily.''



\emph{Except you didn't do anything about Jack when it counted}, I thought.



``We reached out to a number of major powers and sources of information, and you are the ones who responded.  As useful as it might be to have the Y\`{a}ngb\v{a}n or Elite with us, I'm almost glad that we can have this discussion with only those who are truly committed.  Thank you for coming.  I go by Doctor Mother, and I am the founder of Cauldron.''



I could hear a growl from within Faultline's group.  They were directly opposite Doctor Mother, as far away as they could have been.



Probably sensible, all things considered.  Cauldron was to blame for the case fifty-threes.  I suspected they could have handled themselves if anyone in Faultline's group were to attack, but setting a distance between the two groups made sense.



``Look,'' Tattletale said, abruptly, ``Let's cut past the formality bullshit.  I know a lot of you are big on that sort of thing, but we should talk nitty-gritty tactics sooner than later, especially considering the amount of squabbling that's sure to happen.''



``Agreed,'' Chevalier said, from across the room.



``\emph{Mense sterf elke sekonde van elke dag. Babas sterf in die moederskoot en die kinders doodgeskiet soos honde. Vroue word verkrag en vermoor en nagmerries skeur mans uitmekaar om te fees op hul binnegoed},'' the woman with the skull-headed shadow said, her voice quiet and level.  I was startled to see that it was a human skull, now.



``I gave you the ability to understand and speak English,'' a man in the group of twelve said.  ``It wouldn't cost you anything to use it.''



``\emph{Ek sal nie jou tong gebruik nie, vullis,}'' the woman replied, her voice still quiet, though it was flecked with anger, just a bit of an \emph{edge}.



The man sighed, ``Well, I could use my power on everyone else here, but somehow I don't think the offer would be accepted.''



Another person in that group, a woman, spoke.  ``She doesn't believe in using English.  Her first statement was, to paraphrase, `People die every day'.''



``Helpful,'' Tattletale commented.  ``Enough with the bullshit and posturing.  We were brought here for one reason.  Well, a lot of reasons, but the main one that ties us all together is that we've got that monster rampaging around and we're not making headway.  We whittle him down, he heals.  Scion attacks, he teleports, and the golden fool doesn't follow.  So let's be honest, let's talk about this and introduce ourselves before we say anything so we're not completely in the dark--''



``Some of us have identities to keep private,'' the man with the cross on his face said.



``We can't bullshit around about secrecy and all that.  We need to dust off our weapons and the schemes we've been keeping on the back burner and \emph{hit} that motherfucker.  More than half of us have cards we're keeping up our sleeves for a rainy day.  \emph{Someone }needs to bite the bullet and play their card.  And then we need to talk about who plays the next card, when number \emph{five} comes around.  Because there \emph{will} be a fifth.  Or a fourth, if you count Behemoth or not.''



``Many of us are playing on a scale where a particular play would put us at a critical disadvantage,'' the man with the cross on his face said.  ``Acting now, at the wrong time, it wouldn't only hurt us, but it would put bigger things at risk.  There's doing wrongs for the greater good, and there's doing noble deeds and dooming ourselves in the process.''



``You're hardly so noble, Saint,'' Defiant said, his voice a growl.



``I wasn't speaking about me,'' Saint retorted.



``Either way, this is why you're here,'' Doctor Mother said.  ``To negotiate.  With luck, you can barter to guarantee your safety in the future, or ask favors of others, in exchange for whatever it costs you to use whatever weapons or resources you're holding back.''



``\emph{We} can barter,'' Faultline said.  Her voice was hard.  ``Unless you're saying the people who've been creating and hoarding parahumans en masse don't have any cards to play.''



``Unfortunately, Faultline, \emph{we} cannot.  Cauldron, to be specific, cannot.  I have provided this forum for discussion, we can help troubleshoot or support plans, or even provide assistance, but our cards must remain in place.  There is nothing any of you could offer us that would be worth what it costs to act.''



``Bullshit,'' I said.  I could feel anger stirring.  ``No way I believe that.  Even just that portal system you've got, that's enough to change the tide of this fight.''



``Not an option,'' Doctor Mother said.



``Because you're afraid,'' Tattletale said.  ``There's a fear that someone's going to come after you, trace the portal back home.  But there's another, bigger fear, isn't there?''



``Yes,'' Marquis said, from among the group of twelve.  ``And I suspect I know what it is.''



``Contessa here has informed me you do,'' Doctor Mother said, cutting him off.  She was gesturing towards the woman in the suit.  ``Let me assure you, it would do more harm than good to reveal the details.  Especially here, especially \emph{now}.''



``Shit on me,'' Tattletale said.  ``You bastards figured this out.  How the hell did a bunch of prisoners in a jail that's dangling inside a mountain get to figure it out before I did?''



``Hands on experience,'' Marquis answered.



``Panacea,'' Tattletale said.



``Exactly,'' Marquis said.  ``Clever girl.  Well, I'm not looking to stir waves.  I can't disagree with the good doctor, so I'll keep my mouth shut.  Back to business.''



``Damn it,'' Tattletale said, under her breath.  Louder, she said, ``You're sure that this doesn't relate to our Endbringer situation?''



``It doesn't,'' Doctor Mother said. ``The Endbringers are a puzzle unto themselves, independent of every other major variable.''



``That reeks of bullshit,'' Tattletale said.  ``I want to think \emph{you're} bullshitting or you're absolutely wrong and they're connected to \emph{everything}, but I'm getting the feeling it's not.  It's bullshit because it's true?''



``I think we're on the same page, Tattletale,'' the Doctor said.



``Can we progress this discussion?'' one of the robed men asked.



``We can,'' the Doctor said.  ``Thank you for getting us back on track, \emph{Turanta} of the \emph{Thanda}.  Let's open the floor to discussion.  Let's start with the possibility that we might draw from the Birdcage.''



``\emph{Freedom matters little to me},'' the girl with the eerie voice said.  ``\emph{The true end draws nearer.}''



``The end of the world, you mean,'' I said.



``\emph{The end of all things}, \emph{queen administrator},'' she said.



Queen administrator?  \emph{What}?  ``Isn't that the same thing?  The end of the world and the end of all things?  Or do you mean the end of the universe?''



``\emph{It doesn't concern other celestial bodies.  It doesn't matter.  This ends, one way or another.  We and ours will carry on, in some form, whether it happens today or three hundred years from now.}''



``How reassuring,'' Tattletale quipped.  ``You won't help?''



``\emph{I am safe where I am, whether it beyond the Endbringer's reach here or deep beneath the mountain.  I will collect from among the dead, and I will keep them company until the faerie rise from the ruins.}''



\emph{Oh}, I thought.  \emph{She's completely out of her mind}.



``There's no way to barter for assistance from within the birdcage then?'' Doctor Mother asked.  ``Nothing you want, Glaistig Uaine?''



The girl, Glaistig Uaine, responded, ``\emph{A hundred thousand corpses}, \emph{each being one naturally gifted by the faerie.''}



``We don't have time to laugh about like this,'' \emph{Turanta, }the apparent spokesman of the cold capes said.



``\emph{I am not joking, astrologer.  I would like to see their lights dancing in the air.  I have seen only glimmers, fragments of the performance.  To see it all at once\ldots yes.}''



I heard someone in Faultline's group swearing.  Newter, I suspected.



Honestly, I kind of agreed.  I clenched my fists, biting back the worst of my anger.  I managed to stay calm as I commented, ``I'm getting a better idea of why things are as screwed up as they are.  We've got all of the major players here, and half of you are willing to do nothing while the world burns.''



``All of the major players who were willing to come to the table,'' Doctor Mother said.



\emph{Not any better}, I thought, but I held my tongue.  Doctor Mother had turned to the girl from the birdcage.  ``If you participated in the fight, I can promise there would be a number of dead parahumans there.''



``\emph{I fear that would not be enough.  It would need to be all together, for the greatest effect},'' Glaistig Uaine said.



``We could provide that many over a period of ten years, if required, but we'd want more assistance than simply this one fight,'' Doctor Mother said.  She stopped as the man with the glasses leaned close.  A moment passed, ``Or we could provide that many twenty-seven years from now.''



I felt a bit of a chill.  They were so casually discussing this, as if it were possible.



I opened my mouth to cut in, but Glaistig Uaine spoke first.



``\emph{No.  No, I don't think I'll accept.  My word is too vital to me, and you seem to want me to war with the abominations.  I don't fear my own death, but I would rather be together with the others than be separated until the grand celebration.  I won't fight.  I would only grant my advice, some power here and there.}''



Doctor Mother sat back in her seat.  The ominous silence suggested she was still considering it.



A hundred thousand lives, being mulled over so readily.



``That's a shame,'' Doctor Mother said, in the end.



``If I may?'' Marquis spoke up.  ``With your permission, faerie queen.''



``\emph{Granted,}'' Glaistig Uaine said.



``There are others who wouldn't mind being free again,'' he said.  ``Myself included.  We'd fight that monster if you gave us the chance.  All we'd ask is that you let a select few others out, and that you don't create a portal that leads back to the Birdcage after the fact.''



``No,'' Chevalier said, breaking his long silence.  ``No, I'm sorry.''



``Some of the strongest parahumans are contained inside that building,'' Marquis said.  ``Glaistig Uaine is one, but there are others.  My daughter is another.''



``Your daughter was a mental wreck the last time anyone outside of the Birdcage saw her.  There are too many dangerous individuals in there.  \emph{She},'' Chevalier said, pointing in the direction of the woman with the shadowy pet with the massive bird skull, ``Has killed \emph{thousands} of people.  That's nothing compared to what some individuals in the birdcage have done.  We'd be letting the wolves run free again, in the hopes they deal with the lion.''



``If there is no other way to deal with the lion, and we know the wolves have been caught in our snare once before\ldots'' Saint said, trailing off.



``We \emph{know} they can be dealt with.  We're just lacking resources.  Opening the doors of the Birdcage has to be a last resort.''



``Oh, I don't know, I could stand for it to be the first resort,'' Marquis said.  He turned toward the Doctor, ``I'm staying mum about what my daughter discovered.  The details we both know that must not be shared.  Surely that's worth some goodwill.''



``It is,'' the Doctor replied.



I glanced at Tattletale.  Her eyes were moving quickly, hungrily taking in details.



Chevalier sighed.  ``Dragon?  Some backup.''



``I have to say no,'' Dragon said.  ``The prisoners must stay within the Baumann Parahuman Containment Center.  If you intend to rescue them, I'll deploy everything I have to stop you.  Neither of us can afford the losses at this juncture.''



``But if we \emph{did} try,'' Saint said, ``And if we \emph{did} free a handful of deserving individuals, you wouldn't be unhappy, would you?''



There was a pause, telling.  It was enough of a delay for Chevalier to look from Saint to Dragon and give her a curious stare before she spoke.  ``My view on who is \emph{deserving} is far different from yours, Saint.''



``Those of us standing here.  Me, my daughter, Lung,'' Marquis said.



``You cannot speak for all of us on that front,'' a matronly woman spoke.  ``One of my girls was unfairly imprisoned, another is on the verge of losing her mind, in captivity.''



``We \emph{all} have people we'd see freed,'' the man who'd spoken about granting the ability to speak English said.  ``Let's say two for each of us.''



``Thirty six in all,'' Dragon said.  ``One in five of the people currently in the Birdcage, almost.  Six more could potentially use the opportunity to slip out, through Stranger powers or other malfeasance.  Glancing over the notes my artificial intelligences have made regarding the facility, I can guess who some of the cell block leaders would choose to release.  No.  I harbor concerns about the Birdcage, but this is not the answer to that.''



``It would do more harm than good,'' Chevalier said.  ``And I say that with full knowledge of what we're up against here, today.  The last \emph{three }days.''



``Their opinions don't decide this,'' Marquis said.  ``If it were solely up to our officers and jailer in the first place, then we'd be free already.  You, Cauldron, have the means to send us back or not.  It's your authority that matters.''



Chevalier shifted his grip on his weapon, but he didn't attack.  ``We'll bargain.  Marquis is offering assistance, but the PRT has influence.  We'll deal with you, Doctor, if it means the Birdcage remains sealed.  With the ongoing inquisition against Cauldron capes, perhaps there are one or two you'd want to be ignored.  They couldn't be promoted, that's the PRT's jurisdiction, and it would only draw attention to them that I couldn't help them avoid.  Still, I could time a transfer, allow someone to slip through the cracks.''



``A few someones,'' the Doctor said.  ``Yes.  I'm sorry, Marquis.  Our clients must come first.''



``You'll be twisting our arms and escorting us through the portal, then?''



``You'll go willingly.  This place cannot sustain life.  It's a facility in the middle of a wasteland, and your Earth is several universes away.''



``I see,'' Marquis said.  ``Unavoidable, I take it.  And if I were to share the particularly valuable information that you and I both know, that you don't want me to share with others who are present?''



``I can't \emph{believe} I'm not getting in on this,'' Tattletale whispered to me.



Doctor Mother didn't reply.  She remained still, her eyes on Marquis, as the woman in the suit, who she'd called Contessa, leaned in close, whispering.



``You won't,'' the Doctor said, when Contessa had straightened and stepped back, standing guard behind the Doctor's chair.



``I won't?''



``You won't.  \emph{Teacher} would, hearing that, but Teacher has a secret he doesn't want divulged, and he now knows we know.''



Marquis turned, his shadow shifting, presumably as he looked at Teacher.  He turned back, ``Ah well.  I suppose I'll just say we're here if you need us.''



``If we need you that badly,'' Chevalier said, ``Then we've already lost.''



``Rest assured,'' Marquis retorted, ``I think you're doing a \emph{very} good job at getting yourselves to that juncture.''



``It's a failure across the board,'' I said, surprising myself by speaking.  ``All of us, the Birdcage prisoners excepted, we're not doing enough.  If we don't come up with an answer or get someone to step up to bat and fight, then we're doomed.  We've got the end of the world happening in twenty-thirteen, and we can't even band together for \emph{this}.''



``Complaining gets us nowhere,'' Faultline said. ``Besides, it's not like \emph{this} is small potatoes.''



``Okay then,'' I said.  ``Let's talk \emph{resources}.  If you've got parahumans or information, let's hear it.  Let's show a measure of \emph{trust} and have Marquis or Cauldron share the tidbit of information they've gleaned.  Let's talk \emph{options}that don't involve fighting.  Tattletale thinks these bastards are \emph{designed}.  Where's the designer?''



``Nowhere we can find,'' Doctor Mother said.  ``And we have the most powerful clairvoyance we know about, alongside the most powerful precognitive.''



``Does that mean there isn't a designer?'' Faultline asked.  ``That Tattletale's wrong?''



``Get fucking real,'' Tattletale retorted.  ``I'm confident on this count.''



``If they can't find the designer--'' Faultline started.



``There's other possibilities.  Lots of powers confound precogs and clairvoyants.''



``Both at the same time?''



``Be \emph{constructive},'' I cut in.



``We will assist,'' \emph{Turanta} said.  ``\emph{Sifara}, \emph{Bahu} and I, others beneath us in our organization.  I cannot speak for my fellow brothers, but I will ask them because we all owe a debt.  Our brother died, but Weaver helped to make it not for nothing.''



``Phir S\textoverline{e} died?'' I asked, surprised.



``At the hands of the First, very late.''



``I'm sorry,'' I said.



``We owe you,'' he said.  ``As we owe some of the others.  It is your choice how you would use this.''



``You can pay me back by helping,\emph{ }\emph{here},'' I said.  ``You'd be paying us all back.''



``We have the means,'' he said. ``But this hurts us, because we rely on our enemies not knowing what we are truly able to do.''



``If this goes much further,'' I said, ``It might not matter.''



``This is true.  Of each of you but Weaver and Chevalier, we will ask a small favor, after.  Nothing dangerous or painful to give away.  Token gestures, most.''



``Favors make for a good currency,'' the Doctor said.  ``Granted.''



There were murmurs of assent from others.  The woman with the shadow pet didn't respond, but \emph{Turanta }didn't press the issue with her either.



Dragon glanced at Defiant, but ultimately relented, accepting the terms.



The Doctor spoke ``\emph{Moord Nag}?  We could use your assistance.''



The woman and her shadow pet with its crocodile skull looked at Doctor Mother.  ``\emph{Laat hulle almal sterf.  Ek is tevrede om die w\^{a}reld te sien brand en die vallende konings te spot.  }Ek en my aasdier sal loop op die as van die verwoeste aarde.''



``She says no.  Let them all die,'' the woman from the Birdcage said.



``Can I ask who she is?'' Faultline asked.



Tattletale was the one to answer.  I think she got a measure of joy out of rubbing the fact that she \emph{knew} in Faultline's face, ``\emph{Moord Nag}.  Warlord based in Namibia.  As far as the current warlords in the area go, she's had the longest lifespan at about eight years or so, and she's gotten things to the point where most of the other bastards around there are kowtowing, asking permission to attack this city or occupy that area, to go to the bathroom or unite two groups in an alliance.''



``\emph{Die badkamer}?''



``\emph{Us}, basically,'' Tattletale said, glancing at me.  She turned her head to look at Grue, ``Only on a much, much bigger scale, and she did it alone.''



``\emph{Ek het dit reggekry met aasdier},'' \emph{Moord Nag} responded.  ``\emph{Nie alleen nie.}''



``With your pet monster, right.''



``She said she'd be willing to let the world burn, before,'' the woman from the birdcage said.  ``I don't think you have an ally there.''



``From her attitude,'' Saint added, ``I don't even see why she was invited.''



``I'll ask you the same thing I asked the others,'' the Doctor said.  ``What would it take for you to fight, here?''



``\emph{Ek kan nie krag spandeer sonder om die nag lande hulpeloos teen hul bure te los nie}.''



``She can't spend her power, not without--''



``We'll supply what you need to replenish it,'' the Doctor said.



``No,'' Dragon spoke.  ``No, you won't.''



``\emph{Ek sal nie-}''



``It would be appreciated,'' the man from the Birdcage that had granted her the ability to understand English spoke.  ``Reconsider.  Don't underestimate our resources.''



``\emph{Vyf duisend, lewendig, dit maak nie saak of hulle mag het of nie.  `N Fraksie van wat jy die gek aangebied het.}''



``No,'' Dragon said, before the translator could speak.



``Yes,'' the Doctor said, just as readily.  ``I caught the number, I can figure out the rest.  You'll get what you need.''



``I can't stand by and watch this, not like this,'' Chevalier said.



``How many more will die if we don't act?'' the Doctor said.  ``The \emph{Thanda }will counteract the Endbringer's teleportation ability, at least for a time.  \emph{Moord Nag} gives you much-needed clout.  Again, at least for a short time.''



``In exchange for five thousand lives?'' Dragon asked.



``A small price to pay.  How many have died as we conducted this meeting?''



``\emph{Jy praat asof dit saak maak. Die kontrak is verse\"{e}l. Sal ons gaan nou,}'' Moord Nag said.



``What did she just say?'' Chevalier asked.  \emph{Moord Nag }was already walking away, stepping away from the panel and into the recessed passage beside it, almost completely hidden in shadow.  I could only make out the rodent's skull, overlarge and pale in the darkness.



``The contract is settled,'' Dragon said.  ``She sees it as inviolable, now.''



``I \emph{like} her,'' Marquis commented.  ``Mass murder aside, anyways.  Woman of her word.''



``We'll find her,'' Chevalier said, to the Doctor, ``After the battle is done, before you deliver those people to her.''



``You promised us a favor, in exchange for our not letting Marquis and the other cell block leaders free,'' the Doctor said.  ``I could ask you to leave this be,'' the Doctor said.



``No.  Not \emph{this}.  Not five thousand people, fed to that woman's pet.''



``Stop us, then,'' the Doctor replied.  ``Or \emph{try, }as it may be.  That's one Endbringer we should be able to drive away.  As Weaver said, we may have to evacuate the planet if this doesn't work.  Faultline, your assistance would be invaluable on that front.  You've already created nine, I believe?''



``Three of which were supposed to be secret,'' Faultline replied.



``It doesn't matter.  We'll pay for several more, at major locations, and we'll arrange your transportation.''



Faultline stared at the woman.  ``No, Doctor.''



``No?''



``Not your money.  Not \emph{you}.''



``Shortsighted,'' Saint commented.



``I think this is pretty big picture.  Money talks, and I don't like how this money sounds.  She spends five thousand lives like someone else would spend change.  Cauldron made innocent people into monsters.  They took everything from them.  I can't deal with that in good faith.''



She turned to Chevalier, ``We'll give you a discount.  Escape routes in major cities across America.  Leading to the world that the Brockton Bay portal goes to.''



``\emph{Fuck that},'' Tattletale said.



``I'll talk to my superiors,'' Chevalier said.



``Good,'' Faultline said, ``that's settled, then.''



``Leaving only the Endbringer that comes next,'' I said.



``We won't know what measures need to be taken until it makes an appearance,'' Defiant spoke.



``Another meeting,'' the Doctor said.  ``Another day.''



I could feel my heart skip a beat at that.  I wasn't sure I liked what this was becoming.



Then again, the nature of this meeting had been suggested from the start, with the shadows concealing identities.  Everything the PRT had been fighting to assure people that parahumans \emph{weren't} doing was happening here, in this room.  Scheming, trading lives like currency, and wielding incredible amounts of power, money and influence.



``But before we get that far,'' the Doctor said, ``Tattletale?''



``You asked me here for a reason,'' Tattletale said.  ``Multiple reasons.''



``The first being to give you an opportunity to check something for our mutual benefit.''



``You brought the major players in so I could see if anyone was the designer, the creator of the Endbringers.''



``And?''



``Nobody here.''



The Doctor nodded.  ``I suspected.  They remain immune to precognition, but the designer wouldn't be, I don't think.  It's good to double check, regardless.  Will you be attending if we hold another meeting, Chevalier?'' the Doctor asked.



Others, the \emph{Thanda}, were departing, now.  Grue had stepped away from the panel to step close to Tattletale, whispering something.



Then Grue walked past me, not even glancing my way, before disappearing into the corridor I'd used to enter.



Hurt, confused, I couldn't speak to ask Tattletale why without possibly interrupting Chevalier, as he spoke in a steady, quiet voice.



``I don't think I have a choice.  If I don't come, then I'm left blind to what's occurring behind the scenes.  I wouldn't be able to intervene if you tried something like you did with the Birdcage.''



``That's true,'' Doctor Mother said.



``And I think that's exactly what you wanted,'' he said.  ``You have that \emph{Contessa} there, and she sees the road to victory.  You schemed this.''



``Yes.''



``Why?''  Chevalier asked.



``It's not time for you to know,'' she said.



``\emph{Fuck that},'' Tattletale cut in.  Most of the other groups were gone.  Faultline and her group lingered behind.  ``I think it's damn obvious what you're doing.''



``A new world order,'' I said.  Tattletale nodded in agreement beside me.



There were a few curious glances shot our way.  I could see the Doctor shift position.  Exasperation?  Annoyance?



I leaned forward, resting my hands on the railing in front of me.  Grue's odd departure only fueled an anger that had been simmering, ``I had a hell of a lot of time to think, in prison, in my downtime and during stakeouts.  There's only one thing that really makes sense, as far as your motivations go.  It's not the clues or what you're doing, it's what you \emph{weren't} doing.  Only Legend helped against the Slaughterhouse Nine, but he wasn't in the know, from the looks of it.  You didn't help Coil, and you didn't help \emph{against} Coil.  You only helped against Echidna when it looked like everything might go down the toilet.  But Alexandria steps in when I leave, confronts me after I'd surrendered to the PRT.  So I had to ask myself \emph{why}.''



``I can imagine,'' Doctor Mother said.



``We were guinea pigs,'' I said.  ``For what?  So you could be in charge?''



``Not us.  Never us,'' the Doctor said.  ``There's a lot you don't understand.''



``\emph{Try us},'' Tattletale said, almost snarling the words.



``All of this?  It's small scale,'' the Doctor said.  ``Important?  Yes.  But it's nothing in the grand scheme of things.''



I clenched my fists.  ``Five thousand lives, nothing.  Talking about a hundred thousand parahumans to be delivered after twenty-some years, nothing.  The lies you perpetuated with Alexandria, the schemes, \emph{Echidna}, the human experimentation, the case fifty-threes, everyone you watched die just so your experiment with parahumans in charge of Brockton Bay wouldn't be tainted\ldots''



``We'll go down in history as the villains,'' Doctor Mother said.  There wasn't a trace of doubt or hesitation in her voice.  ``But it's worth it if it means saving everyone.''



``You sound so sure,'' Gregor the Snail spoke, from behind Faultline.  He had a heavy accent.  European-ish, in the same vein as \emph{Moord Nag}.



``Do morals matter, if our alternative is a grim and hopeless end?''



``I would never question your morals,'' Gregor said.  ``I know you have none.  I merely wonder why you are so confident you will succeed in all of this, that you will save the world and you will achieve your new world order and your parahuman leadership.''



``We have a parahuman that sees the path to victory.  The alternative to traveling this path, to walking it as it grows cloudier and narrower every day, is to stand by while each and every person on this planet dies a grisly and violent death.''



``You know how the world ends,'' I said, my eyes widening behind the lenses of my mask.



``Of course,'' she answered, standing from her chair.  She collected papers and a tablet computer from the table in front of her.  She collected it into a neat bundle, and the man with the glasses took it from her, holding it under one arm.  Only then did she add, ``We already saved it once.''



There were no responses to that.  Confusion and disbelief warred with each other as I stared at her silhouette.  The others seemed to be in similar straits.



``You had better hurry if you want transportation to the battlefield,'' she said.  Then, with the man with the glasses and Contessa following, she strode from the dark chamber.





