





Khonsu allowed himself to be struck by Alexandria, using the impact to float back at a higher speed.  The act gave him the positioning he needed to draw his spheres closer to the Jaguars' contingent.



A lack of coordination, a simple error, and ten capes were caught, to be killed in moments.  Moments they experienced as weeks, months and years.  Some had brought food and water.  I almost pitied those capes.



\emph{Moord Nag }appeared, riding her shadow's skull like a surfer might ride a wave, except there wasn't any joy in the act.  Her arms remained still at her sides, her head not fully erect, eyes almost looking down, as if she watched the skull with one eye and Khonsu only merited her peripheral vision.



She didn't wear armor.  Her top was a simple t-shirt with the sleeves removed and bottom half cut off.  There was a faded image of a rock band on the front, her bra straps showing through the gaping armholes.  Her dress was ankle length, frayed a little at the edges.  Her feet were bare, her hair in braids and tied back behind her neck.



The skull dipped close to the ground, and the warlord stepped off as though she was getting off an escalator.  The shadow's head had taken on the appearance of a serpent's skull, complete with fangs, and the body was a column behind it, stirring around \emph{Moord Nag} without touching her.



It lunged, and fragments flew off Khonsu's shoulder as the  shadow made contact, rubbed against him.  It was as though the shadow's body were a series of circular saws, a rasp.



Khonsu's field made contact with the shadow's body, catching the middle of its body.  \emph{Moord Nag }didn't even flinch as her serpent was trisected, the middle section dragged away.



The serpent was winding around Khonsu now, maximizing the surface area that was making contact.  Khonsu elected to ignore it, floating forward to put himself in reach of more of the defending capes.



\emph{Califa}\emph{de Perro }used his massive spear to sweep a squadron out of the way before striking the ground, using the impact to throw himself back out of the way.  He landed and straightened.  He was shirtless, and had no doubt oiled his skin, though dust had collected on it, turning him a gray-bronze.  He had bracers with fur tufts near the elbows, and a dog mask that covered the upper half of his face, extending a distance forward.  The only other affectation he wore that made his outfit resemble a costume was the mount at his waist, too large to be a belt buckle, with a molded dog's face jutting a rather generous handspan in front of him.  He smiled, his teeth white and perfect, as the capes he'd batted aside climbed to their feet.



Apparently deeming that the circles weren't working in this situation, Khonsu banished all three.  \emph{Moord Nag's} shadow was freed, and rejoined the remainder of the mass.  Khonsu's forward advance was momentarily paused by the impact.  He created the circles anew, placing them in spots where people at the epicenter couldn't move fast enough to escape.



That was the moment I advanced.



``\emph{Weaver, how the fuck did you get to South America?}''  It was Tecton.  ``\emph{The Director is flipping out}.''



``Someone gave me a ride.  Chevalier will explain later.''



``\emph{You completely dropped off the radar for half an hour.  We were convinced someone had come after you to take revenge for the work we've been doing cleaning up.}''



``Not revenge.  It doesn't matter.  I-'' I stopped short as a fresh circle appeared.  The placement, the timing\ldots Legend had been caught.



``\emph{Weaver?}''



Legend became a blur within the field.  Then, in a matter of two or three seconds, the entire space filled with a red light.  It slowly became white.  Khonsu's power apparently affected \emph{all} of the space above the bubble, reaching into the stratosphere.  It was like a pillar of light.



Eidolon created a forcefield, much like the one he'd fashioned to contain Phir S\textoverline{e}'s time bomb, only this one was open on one side, a `u' shape with the opening facing Khonsu.



Khonsu seemed to notice, because he moved the column.  It intersected Eidolon's forcefield, and Khonsu's power won out.  The forcefield collapsed.  This \emph{wouldn't} be an effect Eidolon could contain.



``I'm in the middle of something, Tecton.  I'm wearing the same camera I had at the last fight, so ask for access to the feed, or get over here.  We think we've got a way to pin him in place.''



``\emph{Right}.''



Eidolon was shouting something I couldn't make out.  Alexandria joined the fray, fighting to keep Khonsu in place, pummeling the Endbringer, dodging the columns that closed in on her.



It was impossible to say exactly how he did it, but Eidolon managed to catch the light before it could turn the battlefield into a smoking ruin.  It condensed into a ball, swinging around past Eidolon as if he were a planet and it was in orbit, and then flew into Khonsu and Alexandria with a slingshot turn.



It wasn't a long, steady stream like the one in New Delhi had been.  It was a white bullet sliding out in a heartbeat, cutting past Khonsu, Alexandria and a good mile of landscape, before driving into the ocean at the horizon's edge.  Steam billowed out explosively.



Eidolon crossed the battlefield in a flash, weaving to the left of one of the two remaining columns of altered time, the right of the next, and erected a wall to keep the steam from frying the flesh from our bones.



It couldn't have been precognition that let him move that fast.  Enhanced reflexes?  Something else entirely?



And he'd been saying his power had been getting weaker.



Alexandria had been stripped of much of her costume, but she fought on without a trace of modesty.  Legend, too, seemed unfazed, unaffected by however many years he'd spent in Khonsu's trap.



And Khonsu, for his part, hadn't suffered nearly as much as Behemoth had.  Five or six layers had been stripped away, and what was left was glimmering with a light that danced around the outside of his body.



The hue and intensity of it matched the light at the edges of his time fields.  It slowly faded.



I reached the battlefield proper, but lingered near the back, beyond the reach of the time fields.  This wasn't a scenario where I'd be on the offensive.  At best, I was a helping hand.  My bugs spread out over the area, and I was able to track the movements of the time fields, the combatants.  I started drawing out the spools of silk I had on my costume, extending them between me and the various combatants, using the arms on my flight suit to manipulate them and ensure that neither I nor my threads got tangled up.



Spider silk extended between me and the various capes around me.  These guys were South American.  Three out of four would be in league with the various criminal factions and cartels.  One in four were `heroes'.  I couldn't tell the difference between them.  The cues and details in their costumes weren't ones I was familiar with.  The choices in color, style, attitude and more were too similar.  A cultural gap I couldn't wrap my head around, in any event.



Things were confused further by the fact that, by many accounts, the villains running or serving within the cartels were the ones sponsored by the government.  The `heroes', in turn, were rogue agents.



\emph{Califa de Perro,} King of Dogs,\emph{ }howled and joined the fight, ready to capitalize on the success.  In the same instant, I sensed my bugs being eliminated.  Not \emph{dying}, per se, but being eradicated from existence.  The ones who'd been following after the column had been caught inside.



It hadn't changed direction.  It had stopped, in \emph{preparation} for a change in direction.  I didn't even have to look to see Khonsu's target.  I caught an earring of the King of Dogs with my silk, tugged.



He stopped, yelping as he looked in my direction.



``Run!'' my voice was no doubt lost in the cacophony.  I tugged again.



He used his spear to move.  A second later, the time field veered into the space he'd just occupied.



It was moving faster.  A third circle appeared, and the movement had accelerated.



Sensing that Khonsu was about to beat a retreat, the \emph{Thanda} made their move.  A piece of rubble descended from the heavens, striking Khonsu with a force that knocked half of the defending capes off their feet, myself included.



Another of the \emph{Thanda }used their power to anchor themselves to the rotating circles.  They floated through the air, equidistant to the circle, effectively untouchable, waiting, watching.



When they reached a certain point in the rotation, they caught a small hill so it could join them, anchored to them as they were anchored to the circle.  It swung into Khonsu like a wrecking ball.



The falling star, such as it was, had broken through more of the exterior.  Not a \emph{lot}, but some.  As the dust cleared, I could see glimmers of light, dancing through the space beneath the injury.



It was the moment I realized that the motherfucker was \emph{reinforced}.  He had forcefields set between layers, so he couldn't be wiped out in a matter of good hits like Behemoth had been.  It was eerily reminiscent of Glory Girl.



Still, he was feeling the hurt.  \emph{Moord Nag's} shadow ripped into the site of the injury, widening it, danced back as Khonsu swung one arm at the skull, clipping and shattering one antler, and then lunged again, driving itself into another injured area.



It caught Khonsu off-balance, and he landed on his back on the ground.  The shadow flowed over him, the skull butting him in the face to knock him down once again as he tried to rise.  It simultaneously extended out, reaching across the battlefield to push \emph{Moord Nag} back out of the way of a swiftly approaching Khonsu-field.  She stumbled a little as she was deposited a hundred feet back, but she didn't really \emph{react}.  The shadow had more personality than she did, here.



Khonsu had apparently had enough, because he extended his hands out to either side, lying with his back to the ground.



The \emph{Thanda} member who was rotating around the Endbringer reached out, and each and every one of the defending capes was swept up in his power, drifting counter-clockwise around the Endbringer.  My feet lifted off the ground as he rose, and all of us rose with him.



The Endbringer teleported, and thanks to the Thanda, we were collectively teleported with it.  My bugs, \emph{Moord Nag's }shadow, and several tinker-made mechanical soldiers were left behind, as we found ourselves on a beach riddled with stones the size of my fist.  Silos bigger than most apartment buildings loomed just over the hill.



The fight resumed in heartbeats, capes closing the distance to fight the instant the Thanda deposited them on the ground.



\sectionbreak



My phone rang. I felt only alarm for a brief second, my blood running cold.



I sighed and struck a key on the keyboard.  The window with the video footage of the Khonsu fight closed down.



I let the phone ring twice more before I made myself check the screen.  Tecton.



\emph{I wouldn't pick up for most others, }I thought.  Hell, I'd have left the phone off if I didn't fear that there'd be a critical call.  I'd seen most of it anyways.  I answered the phone.



``\emph{Weaver}, \emph{where the fuck} did you go?\emph{``}



I smiled a little to myself.  It was an eerie, amusing parallel to what he had said in the video, except he was a little more frayed, a little more weary with me.



``You know where I'm going,'' I said.  ``So do the bosses.''



``\emph{We haven't even- you're going to screw this up for yourself.  Why now?}''



``It's fine, Tecton,'' I said.



``\emph{It's not fine, it's\ldots}''



``They don't have to like it.  I don't think it matters if they don't.''



He seemed to be lost for words at that.



I didn't push the offensive.  I'd been working on that in the therapy sessions, not treating social interactions like fights.  Calm, patient, I dragged my finger down the side of the screen.  The text scrolled down.



\strong{Canberra}, Feb 24th, 2011 // Simurgh\emph{Notes}:  Scion no-show.  Legend/Eidolon victory.
Target/Consequence: See file \underline{\strong{Polisher}}\underline{\strong{ Treatise}}.  See file \underline{\strong{Lord}\strong{ Walston}} and file \underline{\strong{King's}\strong{ Men}}.



\strong{Brockton Bay}, May 15th, 2011 // Leviathan
Notes:  Scion victory.
Target/Consequence: Noelle?  See file \underline{\strong{Echidna}}.  No contact made.



\strong{New Delhi}, July 26th, 2011 // Behemoth
Notes: Scion Victory, ENDBRINGER KILL.
Target/consequence: See file \underline{\strong{Phir}\strong{ S\textoverline{e}}}.



\strong{Flight BA178}, November 25th, 2011 // SimurghNotes: Loss?  Plane destroyed, Eidolon/Pretender drive off Endbringer.  Marks start of guerilla tactics from Simurgh and Leviathan.
Target/Consequence: Incognito Chinese Union-Imperial heir.  See files:\underline{\strong{America/CUI conflict 2012 A}}\underline{\strong{UK/CUI Conflict 2012 A}}\underline{\strong{America/CUI conflict 2012 B}}\underline{\strong{Y\`{a}ngb\v{a}n}}



\strong{Indiscriminate}, January 20th, 2012 // Khonsu
Notes: First appearance.  Scion/Moord Nag victory.  List of all one hundred and sixty three targets and casualty numbers \underline{\strong{here}}.



\strong{L\"{u}deritz}, April 2nd, 2012 // Leviathan
Notes:  Loss?  Driven away by Eidolon.  Secondary targets Swakopmund, Gamba, Port-Gentil and Sulima.
Target/Consquence: \underline{\strong{Moord Nag}}.  Guerilla tactics continue, losses in notable but not devastating numbers, but his target survives.



\strong{Manchester}, June 5th, 2012 // Simurgh
Notes: Defeat, no kill.
Target/consequence: still unknown.  Tie to \underline{\strong{Lord}}\underline{\strong{ }\strong{Walston}}?



Tecton interrupted my scrolling, finally speaking.  ``\emph{I kind of hoped we'd gotten to the point where we were okay, that you'd trust me.}''



``I trust you,'' I said.  ``But-''



``\emph{But},'' he said, echoing me as he cut me off.  ``\emph{Take a second and think about what you say next.  Grace asked me to call because, I'd like to think, I'm a pretty calm, laid back guy.  All things considered, anyways.  But I'm on the verge of being pissed at you, and saying the wrong thing now will push this from me being angry in terms of something professional to me being pissed because of something personal.''}



``I-''



``\emph{Think for a second before you talk, Taylor.  You start talking right away and you'll find your way to a really good argument, and I'll concede this argument, this discussion, but it won't get us any closer to a resolution.''}



``Right,'' I said.  ``Thinking.''



``\emph{I'll be on the line.}''



I mulled over his words.  I was anxious on a number of levels.  Terrified might be the better word.  I stood on a precipice, and the meeting I was running the risk of missing was only part of it.  I continued scrolling down as I thought, as if the individual entries could give structure to my thoughts.



\strong{Rio de Janeiro}, August 15th, 2012 // Leviathan
Notes: Guerilla strike, mind games.  Travels from site to strike Cape Town and Perth after faking retreats.
Target/Consequence: no target apparent.



I stopped at the entry that followed.  I clicked it.  The one for Bucharest.



The video box opened up, but it was dark, the camera covered by my hair at the outset. There was only audio.



``\emph{Oh shit, oh shit, oh shit, oh shit.}''  It was Grace.



``\emph{Are you hurt?}''  Tecton's voice.



``\emph{Golem is.  Shit.}''



The image wobbled as the camera mounted on my mask did, and the \emph{me} on the camera moved the hair aside, allowing the camera to record the video.  The streets were empty, old stately buildings loomed close on all sides, my bugs crawling along the face of each of them.



There was a beep.  The camera was mounted on the right side of my face, the armband on my left wrist, so the glimpse was fleeting.  A yellow screen.



``Heads up!'' the \emph{me} behind the camera called out.



``\emph{For what!?}'' it was Annex responding, breathless.  ``\emph{Oh!  Oh shit!}''



It was only a second later that it became clear just why Annex was swearing.  The city \emph{shifted}.  Roads narrowed, doors splintered and were virtually \emph{spat} out of the frames as the door frames themselves narrowed.



The image on the camera veered.  I'd seen the shift coming, and the bugs on the faces of the buildings let me know that the attack was coming a fraction of a second in advance.  As buildings on either side of me lunged closer together by a scale of five or six feet each, spikes sprung from the elaborate architecture, from gargoyle's mouths at either side of a short flight of stairs, from the sign that bore a store's name, a blade rising from a manhole cover\ldots ten or twelve spikes, for me alone, each fifteen or twenty feet long.  They criss-crossed, came from every direction.



The camera had gone very still.  Then, slowly, it moved again, examining the surroundings.  Blades and prongs surrounded me, poised ready to prick and gouge like the thorns of a rosebush, all around me.  My fingers rose to the camera's view, wet with blood.



I'd only dodged as much as I had by virtue of the ability to sense where the bugs that clung to the blades were moving, and enough luck to be able to move into a space that escaped the various thrusts.  The blood had been from a glancing blow, along the underside of my right breast.  I traced it now, as I sat in front of the monitor, feeling the spot over where the scar would be.  The fucking things were sharp enough to pierce my armor and silk both.



I could remember my outrage at that fact, the stupid, silly comment that had run through my mind, that I'd refused to say in fear that \emph{this} video would somehow leak as well.



\emph{Can't believe the blade hit such a small target}.



``\emph{Everyone okay?}'' I asked, on the screen.



I listened to the various replies of confirmation.  I followed by relating how the armor I'd made them wasn't sure protection.



Then the camera's view shifted as I freed myself of the spikes I'd so narrowly avoided –\emph{mostly} avoided-.  I took two steps forward, and then threw myself to the ground as a figure sprung from the wall, a woman, moving so fast she could barely be glimpsed.  The camera veered again as I rolled on the ground, avoiding two blades that plunged from the underside of her `body' to the ground, punching into the earth.



She had carried forward, uncaring that I'd dodged, slamming into another wall, and she had left a piece of herself in her wake.  Or a piece of what she'd made herself out of, anyways.  She'd \emph{become} the city, and this small fraction of herself had been formed out of the light gray brick that formed the building to my right.  She'd left the pillar behind, three feet across, barring my path.



My head whipped around as I followed her progress.  One more of the rushing figures appeared a block down, two more behind me, simultaneous.  A pillar, then a short wall and another pillar, respectively.



``\emph{Heroes, be advised,}'' Dragons A.I.'s voice came over the armband, ``\emph{The Endbringer Bohu appears to follow a strict pattern.  The city is condensed in twenty-four minute intervals, followed almost immediately by the miniature Endbringers producing barriers, walls, pillars, blocking apertures and more.  The next phase, occurring gradually over the next ten minutes, will produce deadfalls, pitfalls and a smoothing of terrain features.  Following that, we should expect more complex mechanical traps to appear, after which point the cycle will start anew.  Be advised that she attacks with the spikes as she enters each phase.  Disparities in reports suggest that she is feinting in some cases, feigning an inability to do so.}''



``\emph{Good news},'' Annex said, over our comm system.  ``\emph{She can't affect what I'm affecting.  Bad news is I}\emph{wasn't entirely submerged.  I'm bleeding pretty badly.}''



``\emph{We'll get to you},'' Grace promised.



I shut my eyes for a moment.  \emph{Empty promise}, I thought.



There was a distant sound of something massive crumbling.  I now knew it was Tecton, tearing through the area.  I'd be using bugs to direct him to trapped citizens.  I was avoiding the terrain features, he was simply plowing his way through them, doing maximum damage.



The image veered as I approached an archway the Endbringer had created.  I paused before entering, circumvented it by going \emph{over}, avoiding the traps I'd noted with my smallest bugs.



I could see her.  Bohu.  She was a tower, spearing into the sky, gaunt and stretched thin to the point where her head was five times longer than it was wide.  Her body widened as it reached towards the ground, reached \emph{into} it, extending roots and melding into the landscape.  Her narrow eyes were like beacons, cutting through a cloud cover that was virtually \emph{racing} towards the horizon in the gale-force winds.  Her hair, in tendrils as thick around as my arm, shifted only slightly, heavy as stone, despite everything.  She \emph{dwarfed} the other Endbringers in scale, one thousand three hundred feet tall, and her body extended into the city.  I couldn't even guess at the radius she controlled.



Beside her was her sister, Tohu, who would have been almost imperceptible if it weren't for the glow around her.  Tohu, with three faces.  Legend's white and blue mask, Eidolon's glowing shroud, and Kazikli Bey's red helmet, each twisted to be feminine, framed by the long hair that wove and wound together to form her body.  It condensed into cords and ribbons, and the ribbons and cords, in turn, condensed into her chest and lower body, two torsos made with overlapping versions of the hairstuff, small breasted, with only one pair of legs at the lower half.  The colors were extensions of the costumes she was copying, predominantly white here, but with streaks of crimson, green and sky blue highlighting the ridges and edges.



Her four hands were long-fingered, claw-tipped extremities in shapes that served as mockeries of the people she was mimicking.  Two of Eidolon's hands with the blue-green glow around them were holding a forcefield up to protect her sister, while a white-gloved one focused on using Legend's lasers to target capes who thought flying up and out of the city was a good idea.  Not that it was easy to fly in winds like this.  Not the sorts of winds that an aerokinetic like Kazikli Bey could make, capable of slicing someone with air compressed into razorlike ribbons.  A hand in a red gauntlet was gesturing, redirecting the wind to blow down, across, and in crosswise currents that formed brief-lived whirlwinds.



The \emph{me} in the video made a small sound as she took the brunt of that cutting wind, hopped down from the arch, entering the city once more.  It was just now starting her third phase, the pitfalls and deadfalls, eliminating cover, cleaning up rubble, and slowly, painfully crushing anyone who had been trapped in either of the previous two phases.  If crushing wasn't possible, she would apparently settle for suffocation.



I closed down the video.  There wasn't anything more to hear in the exchange between the Wards, and it wasn't a good memory.



Another counter to Scion.  All too often, he was late to arrive, and once Tohu had chosen three faces and Bohu had claimed the battlefield, well, the fight was more or less over.



``\emph{I could hear},'' Tecton said.  ``\emph{You were watching one of the Endbringer videos.}''



``Yeah,'' I said.



``\emph{Thoughts?}''



``We've been through a lot,'' I said.  ``I owe you a lot.''



``\emph{And we owe you in turn.  We're a team, Taylor.  You have to recognize that.  You know that.  We've been together far, far longer than you were with the Undersiders.}''



I sighed and scrolled down.



\strong{Bucharest}, October 10th, 2012 // Tohu Bohu
Notes: First appearance.  Loss.  Tohu selects Legend, Eidolon, Kazikli Bey.  Target/Consequence: see file \underline{\strong{Kazikli Bey}}.



\strong{Paris, }December 19th, 2012 // Simurgh
Notes: Victory by Scion.
Target/Consequence: see file \underline{\strong{The Woman in}\strong{ Blue}}.  See file \underline{\strong{United}\strong{ Capes}}\strong{.}



\strong{Indiscriminate}, February 5th, 2013 // Khonsu
Notes:  Victory by Eidolon/The Guild.  List of the twenty-nine targets \underline{\strong{here}}.



\strong{Los Angeles}, May 17th, 2013 // Tohu Bohu
Notes: Victory by Eidolon/The Guild.  Tohu selects Alexandria, Phir S\textoverline{e}, Lung.  Target/Consequence: unknown.



We'd participated in more than half of those fights.  My eyes fell on the clock in the top right hand corner of the screen.



8:04am, June 19th, 2013



``\emph{Listen,}'' Tecton said.  ``\emph{I'm not demanding anything here.  I just need a straight answer, so I know what to tell the others.  If you say you're not going to be here, that's- I'll understand.  Except not really, but I'll\ldots}''



He trailed off.



``You'll accept it,'' I said.



``\emph{I'm going to lie and say yes},'' Tecton answered me.



I looked at the list of recent Endbringer fights, flicking my finger on the screen's edge to scroll up, then down.



``I'll be there at two,'' I told him.



``\emph{You will?}''  He almost sounded surprised.



``We've been through too much, and you're right.  I can't throw it all away.''



``\emph{I'm glad.}''



``See you in a couple of hours,'' I said.



``\emph{See you, Taylor.  Have a happy birthday.}''



``Thank you,'' I said, hanging up.



\emph{Eighteen, }I thought.  I stood and stretched, swaying a little as the craft changed course.  A two-fingered swipe on the screen showed the craft's course and our ETA.  Another two-fingered swipe returned me to my desktop.



C/D: Endbringer
28:18:44:34



C/D: End of the World
-16:21:56:50



Sixteen days late.  The only person more freaked out than me was \emph{Golem}.



I'd revised the countdown clock to assume that Jack Slash would appear on the date he'd set with Golem.  June fourth was the deadline he'd given, for Theo to find him, to kill him, or the madman would kill a thousand people in some spectacular fashion, ending with Aster and Theo himself.



No appearance, no mass murders.



June \emph{twelfth} was the date the Slaughterhouse Nine had left Brockton Bay.  The day that was supposed to start the two year countdown.



It wasn't supposed to be precise, but watching the clock tick with each second beyond the supposed deadline, knowing that something could be happening in a place I wasn't aware of, the mere thought made my heartbeat quicken, an ugly feeling rise in my gut.



Dinah had confirmed to the PRT that things were still in motion, that it was \emph{imminent, }but the idea was swiftly losing traction.



I'd heard people \emph{joke} about it.  PRT employees who had likened Dinah to the evangelical preachers who promised an endtime, then scrabbled to make up excuses when the date in question passed.



My bugs could sense the insects within the city as the craft descended.  Sand billowed in dramatic clouds the \emph{Dragonfly} settled on the beach.



It wasn't\emph{ my} ship, but the name was a joke, due to the degree Dragon had been sending me this way and that.  Defiant was busy now, so it was mostly her doing the chaperoning, when the Protectorate couldn't oblige.



The ramp finished descending, and I stepped down onto the beach, feeling the sand shift beneath the soft soles of my costumed feet.  I could have flown or floated, but then I wouldn't have felt like I was truly here.



I ascended a set of wooden stairs to rise from the beach to the street proper, joining the scattered residents who lived here.  Men and women on their way to work, starting their day, children on their way to school, many in their \emph{Immaculata} school uniforms.



I walked, taking it in.  The smells, the \emph{feel}, even the subtleties in pace and general atmosphere, they were familiar, comfortable.



Not \emph{good}, but they were things I associated with home.



It was an unfamiliar area, but I had studied the satellite maps.  I no longer wore my tracking device, but the PRT no doubt knew exactly where I was, for just that reason.  If they couldn't monitor the \emph{Dragonfly's} location, they would have found it on my computer.



I could see additions in the distance, the white tower that speared into the sky, the blocky, windowless structure that contained the \emph{scar}.  It wasn't visible, but I knew I could make my way to the crater and see how they'd drawn up a border around it, done construction work underground to contain the contents and keep the water from eating away at the city infrastructure.  I'd read up some on changes in Brockton Bay, had heard more from my dad in our regular visits.



\emph{Here}, the area was marked with graffiti, always in the same variants, no two pieces alike.  Devils, castles, angels, hearts.  I suspected the arrangements and combinations meant something.  The buildings here were new, quaint, the layout intuitive.



And in the midst of it, they'd wedged in space for an addition.  It made for a break in the flow of the footpaths.  It forced an abrupt turn, a hesitation as you tried to work out the way to your destination.  Accord had drawn out the city plans, and the Undersiders had altered it to make room for this.  For a marking.



It fit, somehow, the way it broke the rhythm, the way it didn't really \emph{jibe}.



The fact, I thought with a slight smile, that it irritated.



Two masks, resting against one another, one almost resting inside the other.  One laughing, the other not frowning, but the expression blank.  They were cast in bronze, set on a broad pedestal, four feet high.



I approached, my eyes falling on the objects that had been placed on the pedestal.  Wedding rings, a weather-beaten gold that didn't match the bronze.  Twenty, thirty.  I might have obtained an exact count, but I didn't want to dirty it with my bugs.



I turned, looking around, and saw how the buildings surrounding the edifice were marked with graffiti.  Castles and landscapes with blue sky above.



``I thought I'd see you first, Regent,'' I said.  ``A kind of apology, for not coming sooner.  For not being there at the funeral, if there was one.''



The empty eyeholes of the solemn mask stared down at me.



``I've thought about a lot of things in the time I've been gone.  Framing stuff, stepping back to consider just how fucked up it was that I was spending time with you, condoning what you'd done.  You took over small-time gang lords, I know.  Took over Imp, even.  So why did I let it happen?''



The wind blew my hair across my face.  I noticed that there were people staring, looking at me from the other side of the street.  Whatever.  It didn't matter anymore.



``Then I think about how you went out, and I think\ldots you know, it doesn't balance out.  One selfless deed, after all the shit you did?  No.  But that's your cross to bear, not mine.  I don't believe in an afterlife or anything like that, but, well, I guess that's the mark you left.  When we die, all that's left are the memories, the place we take in people's hearts.''



I reached out to touch one of the wedding rings.  It was partially melted into the surface of the edifice.  I imagined someone could strike it free with a hammer.



Not that I would do that.



``Sounds so corny when I say that, but it's how I have to frame this, you know?  You lived the life you did, with a lot of bad, a little bit of horrific, and some good, and now you're gone, and people will remember different parts of that.  And I think that would sound arrogant, except, well, we're pretty similar on that score, aren't we?  It's where we sort of had common ground, that I didn't have with any of the others.  We've been monstrous.''



I let my finger trace the edge of the wedding ring.



``I've hurt people for touching those.''  The voice sounded just behind me, in my ear.  I jumped, despite the promises to myself that I wouldn't.



Then again, she wasn't someone you could anticipate.



``Imp,'' I said.



I turned around to look at her.



She'd been attractive in that dangerous too-much-for-her-age way before, and to judge by her body alone, she'd grown fully into it.  She was statuesque, wearing the same costume I'd given her two years ago, when she'd been shorter.  A quick glance suggested she'd cut off portions to adjust, wearing high boots and elbow length gloves to cover the gap, and wore a cowl to cover the gaps in the shoulders and neck.  It might have looked terrible, but it fit.  Her mask was the same as it had been, gray, noseless, long, disappearing into the folds of the cowl as the fabric sat around the lower half of her face, with only hints of teeth at the sides marking the mouth.  The eyes were angled, with black lenses, curved horns arching over her straightened black hair.



``Tattletale said you'd be back today.''



``I figured she'd know,'' I said.



``Was it worth it?  Leaving?''



I hesitated.  ``Yes.''



\emph{I hesitated}, I thought.



``I told the others.  They're on their way.''



``Okay,'' I answered.  \emph{Fast response}.



No.  Too fast.  I reached out with bugs, and I sensed the crowd, the way they were standing.



Here and there, there were people who shouldn't have been paying attention to the scene.  A young girl inside one of the buildings with the graffiti-mural on the exterior, holding a baby.  A boy was standing a little too far away to see, but he didn't approach to get a better view.



There were a small handful of others.



I looked at the rings on the memorial.  ``Heartbreaker's.''



``He collected them.  I \emph{uncollected} them.''



``I'd heard he died.''



Imp nodded slowly.  ``Said I would.  I told you I'd kill his dad for him.''



An admission.  I felt a kind of disappointment mingled with relief.  Not a set of feelings I wanted to explore.  I suspected the sense of relief would disappear under any kind of scrutiny.



``People keep prying them loose, but there's usually someone nearby to keep an eye out and get a photo or description.  I track them down and bring the rings back.  Once every few months, anyways.  Kind of a pain.''



``It's how he would want to be remembered, I think,'' I said.



``Yeah.''



No snark, no humor?  I wondered how much of that had been a reflection of her friendship and almost-romance with Regent.



``And you recruited the kids,'' I said.  I used my bugs to track the bystanders, my eyes to note more who fit the criteria.  Boys and girls, some narrow in physique, most with black curls, others with that \emph{pretty }set of features that had marked Regent and Cherish.  Some were fit on all counts, others mingled two of the qualities and skipped a third.  Heartbreaker's offspring, unmistakably.



``I recruited some.  They needed a place to go, and it's kind of nice, having them around,'' Imp said.  ``They're good enough at fending for themselves.  One or two, you get the feeling they're almost like him.  In a good way.''



``I'm glad,'' I replied.  \emph{Glad on more counts than I'm willing to say}.



Then, as I realized that any number of those kids might have taken after their father in the powers department, I was struck by the thought that they might know that, that they might report that relief I was experiencing back to their de-facto leader.



If that was the case, they would also report the way I felt ill at ease, just a little creeped out, as I eyed Imp's followers.



Imp was eyeing me.  I cocked my head a little, the best expression I could give without taking off my mask, hoping it conveyed curiosity.



``I like you better than her,'' Imp said.



\emph{Like me better than who?}  I wondered.  Than Lisa?  Rachel?  I didn't get a chance to ask.  I was distracted as I sensed an approach and turned to look.



``Bitch is here,'' Imp said, noting the turn of my head and the figure at the end of the street, ignoring traffic as her dogs made their way to us.



\emph{Rachel}, I thought.



``She's been going to the fights, helping out here when we send for her.  I haven't been going to the fights, so I dunno how much you've seen her there.  She's been checking in on me, wandering around here with her dogs and scaring the everloving shit out of people until I come to say hi, then she leaves for another few weeks.  I've probably seen her the most.''



``I've barely seen her at all,'' I said.  \emph{Even with the Endbringer attacks}.



The dogs weren't \emph{running}, and it took me a moment to realize why.  There was one dog that was larger than the rest, with half of a bison's skull strapped over the left side of its face, the horn arching out to one side.  Armor and bones had been strapped on elsewhere.  It didn't seem like something \emph{Rachel} would have done, dressing up her dog.  One of her underlings?



\emph{It's Angelica}, I realized.  The dog lumbered forward, moving at a good clip, but certainly not the speed the dogs were capable of when they went all-out.  Rachel was controlling the speed of the other dogs to allow the wounded animal to keep up.



She was riding Bastard, I recognized.  It was different from the others, symmetrical, the alterations flowing into each other better.  Two other dogs accompanied her.  Bentley wasn't among them.



The onlooking crowd, Imp's underlings included, sort of hurried on their way as the dogs approached Regent's monument.  Rachel hopped down as they reached our side of the street.



Rachel was taller, I noted, browned by sun, the jacket I'd given her tied around her waist, a t-shirt and jeans, with calloused feet instead of shoes or boots.  Her auburn hair, it seemed, hadn't been cut in the two years since I'd seen her.  Here and there, hair twisted up and out of the veritable \emph{mane} of hair, no doubt where tangled bits had been cut away.  Only a sliver of her face and one eye were really visible through the hair, a heavy brow, an eye that seemed lighter in contrast to the darkened skin.



And \emph{damn}, I thought, she'd put on muscle.  I'd gained \emph{some}, working out every day, but even with her frame and her natural inclination towards fitness, I suspected she must have been working hard, all day, every day.  Maybe not quite what a man might have accomplished, but close.



``Rachel,'' I said.  I was overly conscious of how we'd parted, of the way I'd left the group and the awkward conversation during the New Delhi fight.  ``Listen-''



She wrapped me in a hug, her arms folding around me.



I was so caught off guard that I didn't know how to respond.  I put my arms around her in return.



She smelled like wet dog and sweat, and like pine needles and fresh air.  It was enough that I knew the new environment had been good to her.



``They told me to,'' she said, breaking the hug.



\emph{They} wouldn't be the Undersiders, I gathered.  Her people, then.



``You didn't have to, but it's\ldots it was a nice welcome,'' I said.



``Didn't know what to say, so they told me to just \emph{do}.  I wasn't sure what to do, so I asked and they told me to hug you if I wanted to hug you and hit you if I wanted to hit you.  Yeah.''



\emph{I'm guessing she only just decided}, I thought.  I'd been gambling by wearing my Weaver costume, but then, I hadn't expected them to converge on me like this.  I would have changed before seeing Rachel.



``It's good?'' I asked.  ``Over there?''



``They're building, it's annoying to get in and out.  But its good.  Tattletale made us bathrooms.  We've been building the cabins around them.''



``Bathrooms are good,'' I responded.



She nodded agreement, as if I hadn't just said something awkward and lame.



``I remember you complaining about the lack in your letter,'' I added.



``Yeah,'' she said.



Wasn't the easiest thing in the world, to carry on a conversation with her.



``Others are checkpointing in,'' Imp said.  ``Just to give you a heads up.''



``Checkpointing?''



``Teleporting, kinda.  Limited.  Um.  We've only got a second, but you should know in advance that they're married.''



``Who?''



But Imp didn't respond.



Foil and Parian appeared in a nearby building, the same building the girl with the baby was watching from.  Two others had arrived with them.



\emph{Them?}  I wondered, mildly surprised.  Then again, it made sense.



They approached, holding hands, and a bear managed to form itself from the roll of cloth Parian had bound to her back, without anyone, the stuffed creature included, really breaking stride.  They'd barely changed, but for a little more height.  Foil carried the crossbow that the PRT was apparently maintaining for her, and Parian had donned less dark colors, though the hair remained black.



The two capes with them each wore red gloves as part of their costume.  I knew who they were from the stuff on the forums.  The Red Hands.  The alliance had gone through, apparently.



``So.  You draw me over to the dark side, and then you flip,'' Parian commented.



``I hope it's working out,'' I said.



She shrugged.  ``It isn't \emph{not} working out.''



``We're fine,'' Foil said.  ``I suppose I should thank you.  If you hadn't left, I don't think I could've come.''



``You may be the only person to thank me for leaving,'' I said.



``Don't be so sure,'' Imp added.



``Huh?''



``Nevermind.''



Tattletale arrived next.  Grue appeared at the location with more Red Hands as she stepped outside.  Where the others had been modest, approaching with a kind of leisure, she almost skipped for the last leg of the approach.  She hugged me briefly, then kissed me on the cheeks.  The mandibles, really, where the armor framed my jaw.  Whatever.



Of everyone, I was least surprised at the changes with her.  Her hair had been cut shorter, and she wore a mask that covered the entire upper half of her face, coming to a point at the nose.  Her shoulders, elbows and knees had small shoulderpads on them, and there was a definition to the horizontal and vertical lines of black that marked her lavender costume.  She wore a laser pistol at her hip, which bounced against her leg as she ran.  PRT issue.  Extremely illegal to own.



``Jerk!'' she said, after she'd kissed me on the cheeks, ``You've barely responded to my fan mail!''



``It's kind of hard to reply to it without drawing attention,'' I said.  ``You don't know how much I wanted the details on what's being going on here.''



``Jerk,'' she said, but she smiled.  ``But I should warn you-''



She didn't get a chance to finish before I saw.



Grue approached.  Of everyone, he was the least changed.  Physically, anyways.



But the Red Hands walked in formation around him, and one, a young woman, walked in step with him, close enough that their arms touched.  They could have held hands and it would have been just as blatant.



I'd faced Endbringers, the Slaughterhouse Nine, I'd taken down who knew how many bad guys\ldots and I had no idea how to face this.



He'd moved on, and I was glad he'd moved on.  He maybe needed someone to lean on, to give him emotional support, and maybe she was that.  I told myself that, I tried to believe it, but I was jealous and hurt and bewildered and\ldots



And I bit back the emotion, approaching, ready to hug.



When he extended a hand for me to shake, I had to fight twice as hard to suppress any reaction to the hurt.  I could tell myself that he'd at least done it before I'd raised my arms to hug him, but\ldots yeah.



I took his hand and shook it.  Then, on impulse, I pulled on it, drawing him forward and down a little, and put my other arm around his shoulders.  Half of a hug, half a shake.



``Happy birthday,'' he said, after I stepped back.



The others echoed him.  Welcomes and happy birthdays.  He'd remembered, but\ldots that choice of words.



I eyed the young woman.  She was a rogue, in the dashing villain sense, wearing a mask around the eyes, and old-fashioned clothes with lace around her ample cleavage.  Her jacket and slacks were festooned with belts, bearing utility pouches and knives.  The glove that wasn't red had a knife attached to each fingertip, a brace around it to keep everything in place.



She met my own gaze with one of her own, a narrow, hard look.



``Oh.  Skit- Taylor, meet Cozen.  Second in command to the Red Hand.''



``Nice to meet you,'' I said.  \emph{They don't really match}.



``Pleasure's mine,'' she said.  ``I'm meeting a legend, after all.''



Awkwardness followed.



And in the midst of that, Imp's statements finally caught up with me.



\emph{I like you better than her}.



\emph{Don't be so sure}, Imp had said.  Well, Cozen would be happy I'd left.



Then, with a realization like a dash of cold water to the face, I remembered.



\emph{They're married}.



``Taylor,'' Tattletale said, rescuing me before I could say something dumb.  She hooked her arm around mine and led me around and away.  ``Much to talk about.''



``The end of the world,'' I said.  ``Endbringers.  Finding Jack, or the designer-''



Safe topics, somehow more reassuring than \emph{this}.



``I don't know,'' she said.  ``Everyone's playing it safe, keeping things quiet.''



``What do we do?''



``What was the plan?'' she asked.  ``When you came?''



``I've got six hours before I need to be in New York.  They're swearing me into the Protectorate.''



``Congratulations,'' Grue said.  He sounded genuine.



``I should be saying that to you,'' I said, glancing at him and Cozen.



``Oh.  Thank you,'' he answered, in his characteristic eerie voice.  I couldn't read his tone, and felt a little grateful that at least \emph{one} of us was spared sounding awkward.



``Six hours,'' Tattletale said.  Another rescue.



``I was going to visit everyone in turn to catch up, visit my mom, then see my dad.''



``Well, we're all here.  We can go somewhere together,'' Tattletale said.  ``There're stories to tell, I'm sure.''



``I'm sure,'' I said.  I almost wished my original plan had gone ahead, that I could have a really \emph{short} visit with Grue, a longer sit with Rachel and her dogs, then a long discussion with Tattletale about what was going on, before I headed off to see my mom's grave and my dad.



``Come on.  We'll walk, see the sights,'' Tattletale said.  ``figure out what to do for breakfast or brunch.''



``Okay,'' I said.  I glanced at the others.  Would they be down, or would they back out?  Parian and Foil weren't close to me, but they were sticking around.  Cozen wasn't making an excuse and leaving, and neither was Grue.  I could see him exchanging murmured words with her.



I must have looked a little too long at him, because Imp fell in step beside me.



I glanced at her.



``I was just fucking with you,'' she whispered.  ``I thought you probably deserved it.''



My stomach did a flip flop at that.  Anger, relief, bewilderment, more anger.  Still more anger.



``Man, the way your bugs reacted.  Hilarious.  You act like you're all stoic, but then I just have to look over there and over there and I see bees and butterflies circling around like eagles ready to dive for the kill.''



I opened my mouth to say something, but she cut me off.



``She \emph{is} pregnant,'' Imp said.



My mouth shut.



``Kidding.  This is \emph{fun}.  Come on, butterflies, I see you over there.  Do your worst, I \emph{know} you want to kill me.''



I considered jabbing her with my taser, and the thought was vivid enough that I imagined it buzzing at my hip.



Except it wasn't my taser.  It was my phone.



As it had so often this past month, I felt my heart leap into my throat, that pang of alarm.  A very different kind of alarm than Imp had been provoking from me.  More real, more stark.



I drew the phone from my belt, then stared down at the text that was displayed.  A message from Defiant.



``Endbringer?'' Rachel asked.  Something in my body language must have tipped her off.



I shook my head, but I said, ``Yes.  Sort of.''



``Sort of?''



``An endbringer with a lowercase `e','' I said.  ``It looks like Jack may have made his challenge to Theo.  It's starting.''





