





\strong{July 8th, 2011}



``.\emph{..The reality is clear.  The repercussions of what happened today will change the relationship between hero, villain and civilian.  It remains up to them to decide whether it will be a change for the better, or a change for the worse}.''



``Pretentious, isn't he?'' Jack asked.  He was naked, covering himself with both hands, sitting on a metal bench with more brushed stainless steel behind him.  With the angle of the device, he faced the ceiling.



``Likes to hear himself talk,'' Bonesaw replied, agreeing.  ``Which do you think it'll be?  Change for the better or change for the worse?''



Jack only smiled, his eyes crinkling a bit at the edges.  He was getting older.  It was reassuring and spooky at the same time.  \emph{He's the daddy}\emph{of the group and I'm the kid and he's getting older which makes him more daddylike.}



But it meant he moved slower and got tired more easily.  It was only a matter of time before he made a mistake, lost a fight.



``It's a given?'' she asked.  She pressed the button, and the lights started to flicker again.



``I think so,'' Jack commented.  ``But I almost hope things \emph{do} turn out well.''



The flickering steadily increased.  The progression had to be slow, or they could set off a cascade cycle and overwhelm the power cell they had liberated from Toybox.  If \emph{that} happened, then the shell that was keeping this reality together would break, the holding grid for the pocket dimension's substrata would become fluid and leak out into other hardened realities.  They would likely be crushed by the air, pulped as gravity twisted into eddies and condensed points of hyperconcentration.



Which would be \emph{funny, really}.  A reckless, violent, unpredictable death would be awfully ironic, really.  An artful death, almost, in an anticlimactic way.  It would be better if there was an audience, if anyone could even know and tell the story.  But art wasn't art without an audience.



``Makes for a greater fall?'' she asked.



``Exactly,'' Jack replied.  He had to raise his voice to be heard over the whine of the generator.  ``I guess we find out soon!''



She laughed in response, giddy with the idea, with possibilities, ideas.



Then she pulled the switch.  In a heartbeat, Jack was frozen in stasis, contained.



She walked over to the computer.  Flowers, rainbows and gray-green smiley faces with the eyes crossed out in death bounced around the screen.  She moved the mouse to end the screensaver, giggles still periodically finding their way out of her mouth.



She set the timer, the alarm clock for the stasis to end.



The giggles trailed off.



Silence.



The lights slowly flickered back to life, and Bonesaw found herself standing in front of the keyboard.  The smile fell from her face.



Jack had assumed she would freeze herself.  The empty pod reinforced the idea.



Except\ldots she was telling herself she had to be there to wake them up, and that wasn't wholly true.  It was smart, but it wasn't true.  She wasn't one to be \emph{afraid} of something, but she felt a touch of trepidation at the idea of entering stasis without someone to handle the exit process, without assurance she would wake up.  That was without touching on the issue of the power cell, watching that things didn't go tilt with the pocket dimension.



No, that wasn't wholly true either.  It was a one percent chance.  Five percent, if she counted her lack of knowledge about other tinker's stuff.  But she hadn't touched it, even to move it.  It \emph{should} be safe.



Her eyes tracked the rows and columns of incubation chambers.  They weren't her field either.  A different row for each member of the Slaughterhouse Nine, past or present.



King
Screamer
Harbinger
Breed
Crimson
Gray Boy
Nyx
Psychosoma



There were ten of each in various glass chambers. The original members.



With many, \emph{many} more besides.  She looked down the length of the room.  Most members of the Nine had lasted only weeks or months.  She could count the ones who'd lasted longer than that on the one hand.  A shame she didn't have samples for all of the past members, but she had most of the good ones.



Her, Jack, Mannequin, Siberian, Shatterbird.



Crawler had managed pretty well, too.



He'd been a doofus in the end, though.



She smiled.  It would be a family reunion, really.  But there was work to be done.



They'd come out blank.  Wouldn't do.  She had access to some of the toys they'd liberated from the Toybox.  She'd have to put the new Slaughterhouse's memories together herself.  Brains.  Memories, or things close enough to memories.  She had notes and records, all of the bedtime stories Jack had told her as she drifted off to sleep these past few years.  There was information saved on the computer.  She could hodgepodge it together.



This would be \emph{real} art.  How well could she rebuild them?



Cranial had been selling memories on the black market, selling skills.  She'd kept bad memories too, took them from people, even gave them to some people.  Silly, really.  A lot of them had wanted trigger events, except the trigger events didn't work like that.



This computer was only an access point.  The other computers took up vast amounts of space, out of sight, out of mind.  If something failed, she'd have to go fix it, but she would spend most of her time here, surrounded by her family, some she'd never met.



Mannequin had lost his wife and children in a Simurgh attack.  How to approach it?  A file here, with a woman who had lost her spouse and children in a car accident she'd driven.  Close enough.  She could leave gaps and it would fill in all on its own.  Build it all on a foundation of an academic background, a doctor with confidence to spare, an architect in the same vein, a celebrity singer who'd come in wanting inspiration at the press of a button\ldots run everything in parallel, with the ideas of the former two and the experience of the other\ldots



But that wasn't enough.  He'd been driven, haunted.  How was she supposed to put it all together?  Could she make it a recurring idea, so this Mannequin-clone would see the events flashing before his eyes with every waking moment?  Something he could only quench with a quiet, cold rage?  Or was it something he'd put behind him?



Winter had been an arms dealer, sadistic, ruthless, \emph{cold}.



Bonesaw giggled at the private joke.  The noise echoed in the utter silence.  It was quiet enough that she could hear her own heartbeat and the blood rushing in her ears, the creak of her muscles shifting, even.  That wasn't anything she had enhanced.  Humans simply never experienced true quiet.  Those that had come close tended to go insane.



Another giggle, smaller.  No worry on that score.



How to model Winter?  She wasn't truly a person who created or manipulated cold.  It was a different power.  A \emph{dampening} power, causing objects and people both to lose inertia.  The ambient effect was one of altered physics, the effect on people was one of \emph{will}.  The woman had gained power, money and more, and she'd found she liked tormenting people as much as anything else.  She'd turned to the slave trade, then crossed paths with the Nine.



How to make the Winters with the materials she had?  A child that had a gun in her hand before she could read, someone who had found the drive necessary to rise above her roots, meeting all expectations.  She'd taught herself numbers and business, she'd ruthlessly eliminated competition, and then when she had everything she'd wanted, she had stagnated, rotted like an overripe fruit.



Searches for keywords in Cranial's notes failed to turn up any of the necessary elements.



``Hey, Blasto, buddy,'' she said, and her voice sounded artificially chirpy, even to her.  She looked at her minion, who stood at the other end of the desk, staring off into space, his entire body rigid.  A tear was running down his cheek.



Would have to cauterize his tear ducts, maybe.



``Speak,'' she ordered.  She tapped a key to open a menu, then released the lock on his lung control and breathing.  ``Try now.''



``Ungh,'' he rasped.  ``Ugh.''



Would have to exercise his vocal cords, or he might lose the ability to speak.



``It's too quiet.  Let's see\ldots do you know the theme song to Love Bug?''



``Ugh.  Guh.  Fuh- fuck-''



She hit the key to lock him down, feeling irritated.



``Swearing is so crass!  Okay.  Guess you don't know them.  Let's see.  I've got something in my backpack\ldots''



It took only moments to rig.  Her spider boxes ran on interconnected lumps of gray matter, basic impulses, motor control and storage, with some computer chips to handle functions that were more trouble than they were worth to implement.  One of those chips managed rote movements.  She removed a defunct spider box from the backpack she was keeping beneath her desk and attached it to Blasto's spine, between his shoulder blades.



Overriding motor control, rote movement operation, hook it to the lungs and mouth, tongue, jaw\ldots



Her hands were crimson halfway up to the elbow by the time she was done setting it all up.  She handed the task over to a spider box to handle stitches and cauterizing the bleeds.  A quickie job.



Would be better with a real eyeball, but she'd settle for a camera.



She set a video to play.  Furry cartoon bugs with hearts, peace symbols and other icons on their backs began to dance with cartoon children.



``Love bug love hug!  A, B, C, D!
There they are, coming to say hi!
Love bugs are here, no need to cry!
When you're feeling lonely, when you're alone,
Who can you count on, to be in the zone?''



\emph{``Get a love bug love hug!'' }Bonesaw sang along, pulling up a chair.  She used a pencil to press the buttons on the keyboard so she didn't get it mucky.  Few things were quite as fun as letting the blood dry and then peeling it all off in one congealed strip.



Behind her, Blasto watched the video.  She set it to repeat, and the bug box kicked in the second time around.  Blasto's reedy voice sang along.  It was so pathetic and mournful that she laughed aloud.



\emph{Better give him some exercise too}.



By the time the fourth repeat had finished, he was all set up.  He started dancing along with the fifth, mimicking characters on the screen.  Each repeat would be a little more precise, as the camera captured the necessary elements.



There.



Something to occupy herself with, for the next year and a half.



\sectionbreak



\strong{September 28th, 2011}



``I'm going to take over the world!''



``Wonderful,'' Bonesaw commented, feigning a cultured voice.  ``More tea?''



``Tea, yes!  Obey, serve me.  Give me tea.''



Bonesaw dutifully poured a beakerful of hot water into the cup, then set a spoon by the saucer.  ``No milk?  You're sure?''



``Milk is for weaklings and children.  I'll drink it black,'' Damsel said.



``We \emph{are} children, Damsel.''



A biologically seven year old Damsel of Distress glared across the table at Bonesaw as she took a sip, then had to momentarily steel herself to keep from making a face.  Her face was gaunt, but that was her natural appearance.  Her pale blue eyes deep set, platinum blond hair simultaneously fine and thick, matted together.  The chemical stew the clones were growing in didn't make for typical looking hair growth.



``I could \emph{end} you, for that insult.''



``Yes,'' Bonesaw said.  ``But then you wouldn't have anybody to pour you tea.''



``This tea is too hot anyways.''



``I'll strive to do better,'' Bonesaw said.  ``World domination, hm?  Sounds like a bother.''



``It's my natural place.''



``Maybe,'' Bonesaw said.  ``Well, I don't envy you.  You'll need to hurry, too.  World's going to end soon, I think.''



``I'll rule the ashes.''



``I see.  That's even harder, isn't it?  If there's no way to communicate, then how do you manage it all?  There won't be phones or internet after everything else is gone.''



Damsel's forehead furrowed in concern.  ``I'll delegate.''



``Can you trust the people you delegate to?''



``No.  I trust nobody.''



``Well,'' Bonesaw said, pausing as she took a sip of tea.  ``That's a problem.''



``Yes,'' Damsel agreed.  She swayed in her seat for a moment, then gripped the table with foot-long, clawed fingers to steady herself.  Bonesaw's design, replacing the skeletal structure.  A way to channel Damsel's power and -if needed- briefly shut it off.



``I put a little something in your tea to help you sleep,'' Bonesaw commented.  ``Best to see you off to bed.''



``I'm not\ldots''



``Not sleepy?  You're going to faceplant in your tea.''



Damsel's confusion became a swift, violent anger.  ``You \emph{poisoned} me, wretch!''



``Yes.  I thought you didn't trust anyone.  What a shame that you couldn't be \emph{constructive} in that distrust,'' Bonesaw said.  She stood and walked around the table, then took the little girl's hand, leading her back to the incubation chamber.  The girl obeyed, though she spat epithets.



``I'll flay your skin from your bones, irrevocably destroy everything you cherish,'' Damsel said, her voice fainter.  ``You'll cry your rage to the heavens until your torment subsumes everything.  Madness will be a refuge.''



She was virtually whispering by the time she was done.



``Yes, sweetie,'' Bonesaw answered, dropping the fake accent.  She leaned forward and gave Damsel a kiss on the cheek.  Damsel blinked, as if in slow motion, opened her eyes briefly, then shut them.



A press of a button and a flick of a switch bid the glass case to rise and surround Damsel before she could tip over.  The tube rapidly filled with a soupy liquid, rich in nutrients.  Damsel was fully asleep before the fluid raised her from the ground to float buoyantly in the middle of the tube.  Her tea party outfit billowed out around her, making her look like a jellyfish in the pale lighting.  Her hat, a wide-brimmed, shallow-topped hat with a false flower on the ribbon, drifted off her head and gradually sank to the base of the tube.



She sought out the other clone, finding him at the far end of her lab.  He was a boy, narrow, with long blond hair and a very worried expression.  A complex pyramid of beakers and glass measuring cups was arranged around him.



He was muttering to himself, ``Wall them in.  Wall myself in.  Wall them in.  Wall myself in.''



``Come on, A.G.,'' Bonesaw said.  She reached through the structure and took his hand.  ``Out through the door.''



``Not a door.  Trap.  Safest way to ward off attackers.  Used my hair, made a tripwire, tying ends together.  Maximum devastation if intruder breaks perimeter.''



``Through the window, then.  I'll wall you in.  Promise.''



He nodded.  With excessive care, he climbed on top of the jars that were precariously balanced on one another and slipped out through another aperture in the arrangement, higher up.  He stumbled as he landed.



``This way.  We'll wall you in.''



He followed obediently.  ``Where's my Catherine?  She's my\ldots''



``Your \emph{mom}, silly billy.''  \emph{Cognitive dissonance would be bad.  He could lash out}.  Not that he was that dangerous, like this.



``I was going to say wife.  And I have two children.  They're seven and five.  Except \emph{I'm}\ldots''



``You're seven.  You're thinking of your sisters.''



``I'm confused,'' he almost mewled the words.  ``It hurts, so much of it hurts to think about.  I- I let a lot of people down.  I can feel their disappointment like\ldots like it's pressing in on me from all sides.  I can't hide from it and I can't stop myself from caring.  I-``



``Hush,'' she said.  ``It all gets better when you wall yourself in, doesn't it?''



He nodded mutely.



``Walling you in,'' she said, as she put him on top of the stand.  A press of the button raised the glass enclosure.  She could see him relax a fraction at that.



\emph{A bit of a problem}, Bonesaw mused, as the container filled with the nutrient fluid.



Various elements that were unique to every individual served as a signal that the passenger could reach out to in an attempt at reconnecting with a host.  DNA, electromagnetic patterns, patterns she could barely measure with instruments, all contributed, none was absolute.  Once the connection was established, powers were possible as well.  A moment of trauma sped the process along considerably.  Her initial assumption had been that coming to life would be enough for the clones.



But the clones were dreaming, and those dreams were founded in the fabricated memories she was providing.  It was something of an art, an interesting experiment, to strike all the right notes, to get geography and birthplace right, culture, custom, habit and every other detail, along with the major, defining moments of their lives.



The \emph{Corona Pollentia} was developing as the originals did, drawing from DNA to form as a lobe in the brain, right from the outset.  The dreams formed the connections between the \emph{corona} and the clone.  The bonds were forming too quickly and easily.



It was interfering with the cloning process, as the passenger's typically indistinct and subtle influence on the subject was becoming rather dramatic.  The brain was too pliable while the clones were in their formative ages, the passenger too insistent.



She'd have to scrap everything.  Wipe them clean, grow a new batch of clones.  Nearly three weeks of work down the drain.



Already, she was figuring out how to solve the problem.  She'd have to stagger it, introduce memories in phases, starting with earliest and working her way forward.  Maybe it would be easier, organized.  She could consider each member of the Nine in turn and decide if they had been treated well as babies, if their home and school lives were comfortable\ldots that would be a yes for someone like Mannequin, less so for Ned, for Crawler.



She typed on the computer for a minute.  Special disposal procedures for Crawler.  The rest could be boiled to death.



She watched until the bubbles started to rise.  One or two woke.  It didn't matter.



She returned to her makeshift bedroom.  There hadn't been a mattress, so she'd made a hammock instead.



Blasto lay on the floor.  His voice was barely audible.  He couldn't stand, and his attempts at trying to dance were scraping his arms against the floor.



``\emph{Bug\ldots hug.  I, J, K, L.''}



``Forgot to turn the music off,'' she said.  She found the smartphone and switched off the music.  ``Have a bit of an errand.  Sleep for now, I'll patch you up when I get back.''



Her hair dyed black, a bit of makeup and clothes made the same way she'd made her mattress, creating a lifeform that could spin and ink fabric.



A touch roughspun, but it would do.



She found the remote and hit the button.  There was a quiet \emph{whoosh}, and she was on the other side.



Back in Earth Bet.



Her heart was pounding.  If Jack found out about this, he'd be \emph{furious}.  The risk, the idea that someone would be checking this one spot for a signal, or using a parahuman ability to search for her \emph{here}\ldots



But, she thought, she needed supplies she couldn't make on her own.  Resources, information, materials.



She entered a small grocery store.



``Good morning,'' the man at the counter said.  Thirty-two or thirty-three, to judge by his appearance.  His hair was too long in the back, just starting to recede in the front, his stare intense, but he wasn't unattractive otherwise.



``Good morning,'' she responded, upbeat.  \emph{Don't talk to me.  It would be messy if I had to kill you}.  She corrected herself.  \emph{I'll fix your hair and then I'd kill you}.



``We don't get many new people here.  Kind of out of the way.''  He smiled.



``Driving through,'' she said.  ``My mom is shopping down the street.''



``Dollar store or the boutique?''



``Boutique.''



``Don't blame you for not wanting to go,'' he said.  ``Let me know if you need help finding something.''



She made her way through the store.  Lemon juice, vinegar, sugar, salt, a box of Frooty Toots, some milk, pancake mix.  Nutrient slop was great when she needed to work without cooking, but it was still \emph{slop}.



Glancing up, she could see the man at the counter looking at her in the mirror that had been positioned to give him a view of the aisle.



She wondered momentarily if he'd recognized her.  No, the reaction would be different.



A distrust of outsiders?  No, he seemed too at ease for that.



Something else, then.



She felt more at ease, realizing what it had to be.



She deposited the things on the counter, then paid.  He bagged it and she waved goodbye as she left, offering him a winning smile.



She'd need to stop by a library, there were a few things she needed to look up.  There wasn't enough information on Harbinger, for one thing.  King's background was another blank.  People Jack didn't talk about much, even if he talked about them fondly.



He'd be so \emph{pleased}, she could imagine, if she hit the right notes with them and got their basic personalities right.



Then she could buy clothes and sheets. If there was a good hardware store, she could imagine some tools that would serve.  Her scalpels were getting dull.



This little bumhole of a town didn't have much, and she'd seen maybe one car on the road since she had arrived, but still, she looked both ways before crossing the street.



A pale, dark-haired woman stepped out of the bank, wearing a black suit.



Her attitude, her demeanor, casual.  Nothing combative in the slightest.



Bonesaw still felt a twang of alarm.  The timing with which she'd appeared, the way the clothes didn't fit the area\ldots



Better to guess and be wrong.  ``Are you picking a fight with me?''



``No,'' the woman replied.  ``No I'm not, Bonesaw.''



\emph{Gosh darn ding darn\ldots golly}.  Jack was going to be \emph{maaaaad }if he found out about this.



``Because if you kill me, it doesn't change anything.''



``You worked a biological key into the transporter device.  Unless you are alive, calm and holding the device, it won't work.  It will only transport you.  We can't use it to get inside, and killing you wouldn't stop the stasis period from ending.''



``Yeah.  That's why.''



``I understand.  But I wasn't sent here to assassinate you.  We \emph{could}.  We could even reach Jack, I think, now that we know where to make an entrance.  Still, that's a dangerous prospect, putting powerful parahumans in the same space as a man who's been prophesied to end the world.''



``I'm not a pushover, you know,'' Bonesaw said.  She stabbed a finger in the woman's direction.



It would be so easy to fire a poison needle into her throat.



``I only want to talk.  I'll ask a favor, then leave you alone,'' the woman said.



``You don't know how the Slaughterhouse Nine work, do you?  We don't \emph{do} favors.''



``You'll do this one.  The Slaughterhouse Nine you're mass producing, you're going to install a control switch.  You'll give that switch to me.  Not soon, but later.  Later than you think.''



Bonesaw laughed, high and shrill.  Then she laughed some more.



The woman only waited patiently.



``Silly!  You couldn't be more wrong,'' Bonesaw said.  ``Betray Jack?  Betray the others?''



``You will.''



Bonesaw laughed again, not for quite so long.  Through the giggles, she said, ``If you're going to try to mind control me, I can tell you you've got another thing coming.  I've got safeguards.  You'll only activate my berserker mode.''



``No mind control.  There's a great deal at work here, and this is the best way to go about it, even with the blind spot looming.''



``That's the best argument you can give me?''



``No.  I can tell you two things.''



Bonesaw raised her eyebrows, smiling.  ``Two things?''



``Breadth and Depth.''



``I don't get it.  Those are the things?''



``No.  There's another.  Each of these things is a sentence, an \emph{idea}.  The second sentence is simple.  \emph{Say goodbye}.''



Bonesaw bristled.  Mechanical traps, spring-loaded needles and venom venting systems readied throughout her body.  She let the bags drop to the ground.



The woman didn't attack.  Instead, she turned to leave.



An empty threat?



She debated firing her hollow needles at the woman's back.  But if she missed, she'd be largely unarmed.  She'd have to get even closer to use a venom spray, or poison spit, or her telescoping humerus with flesh dissolving acid capsules beneath her fingernails.



The woman entered the bank, and Bonesaw hurried across the street to follow.



But her quarry was gone.



\sectionbreak



\strong{January 20th, 2005}



Riley panted for breath.  Her body wasn't listening, now.



She reached her mommy's room, then collapsed on the floor, head turned towards the foot of the bed.



The carpet was stained with blood.  On it, just beside the bed, her mother lay face down, head turned to one side just like Riley's was.  She was covered in stitches.  There wasn't a place where Riley could have reached out and placed a hand down flat without touching one of the marks.



An entire row had been cut open, the stitches severed, from temple, down the side of her throat, along the side of her body to her pelvis.



Too much blood loss.  Her mind leaped into action, reaching for knowledge she hadn't had earlier in the night, knowledge of how to fix people.  She took in details, grasped everything from the amount of blood her mommy had to heart rate and the amount of air she was breathing, just from the clues in how fast the blood flowed and the color of the skin.  She knew the order she'd have to fix things.  Ideas fired through her mind, telling her how to close the wounds, to draw the blood out of the carpet and clean it, or even making something that would do the same thing blood did, out of water and some junk from the kitchen, all with the exact right amount of electricity, to fill the veins and carry a low amount of air throughout the body, staving off the shut down of her brain long enough for Riley to figure out something else.



But she was too tired.



``Hurry,'' Mister Jack's voice was almost gentle.  ``You have time.  You can fix her, can't you?''



She could.  Maybe she even had the strength to do it, to get downstairs and climb up onto the kitchen counter to get the things she needed out of the cabinets, and get back up here.  She could cut the lamp cord and use the frayed end with\ldots with a lot of salt, to get the right frequency.



But she was too \emph{tired.  }The moment she was done saving her mommy, she'd have to run to the bathroom and save daddy.  Then she'd have to run downstairs and save Drew.  After that she'd save Muffles, and hurry back to mommy.  In each room, one or two scary people waited for her.  Waited and watched while she worked, then undid her work or came up with worse things to do.



She knew because she'd been doing this for hours.



``Come on,'' Mister Jack whispered.  ``You can do it.  Don't you love your mommy?''



She stared across the room at her mommy.  They were lying with their heads pointed in different direction, so her mommy's face was upside down, almost covered with as many stitches as skin.



She'd done a bad job, she knew.  She couldn't even cut a straight line with the scissors in school, how was she supposed to do \emph{this}?



Mommy mouthed some words, but the stitches pulled her lips in funny directions.



She thought maybe she knew what mommy was saying.



``No,'' she told Mister Jack.



``No?''



``I don't love her,'' she answered.  She blinked, slow, so she wouldn't have to look her mommy in the eyes, and tears were squeezed out.



``Alrighty,'' Mister Jack said.  ``\emph{Say goodbye}, then.''



\emph{Say goodbye}.



``Goodbye, mommy,'' Riley said, obediently.



Silent, her mom mouthed a reply.



It took a long time.



A long, long time, watching the blood volume tick down, seeing how the breathing rate changed, and the heartbeat slowed.  Knowing how the brain would be affected, knowing what the organs were doing, and the order they were shutting down.



At some point, it ceased to be mommy, became something else.  A moment when her mommy became only a dying thing, a machine of flesh and blood that was winding down.



It was easier.



Didn't make her chest hurt as much.



Lips that had been fixed up with imperfect stitches mouthed one final sentence.



``There we go,'' Mister Jack whispered.  ``\ldotsThere.  That's it.''



For a little while longer, the three of them rested on the floor of the room.  Mister Jack, Riley, and her mommy.



Others appeared in the doorway, casting the room in shadow.



``She done?''



``She's done,'' Mister Jack said, standing.  He stretched.  ``As for what we do with her, we-''



He broke off as the clown in the hallway laughed, an eerie, offbeat sound that seemed to be missing something most laughs had.  It seemed to take Jack a moment to gather why the clown had laughed.



When he looked down, Riley was looking up at him, smiling.  It was a forced expression.



``What's this?'' Jack asked.  He smiled back.  ``Something funny?''



``No.  I just\ldots I wanted to smile.''



``Well,'' he said.  ``Me too.  Let's smile together.''



She looked momentarily uncertain, but kept the strained smile in place.



``Yes.  Come with us.  We'll keep you safe.''



She didn't want to.  She wanted nothing less.



But she had nowhere else to go.



``Yes please,'' she said.  ``That\ldots that sounds nice.''



Her mother's final words rang through Riley's head, the last words she'd before she had become a machine that had stopped working.



\emph{Be a good girl}.



She'd be good.  She'd be polite and cheerful and she'd do her chores and she would mind her manners and she'd eat all of her dinner and she'd keep her hair nice and she wouldn't swear and\ldots



\sectionbreak



\strong{November 15th, 2011}



She woke from a nightmare that was becoming all too familiar.  Usually it was only a few times a week, fragments.  Now it was more distinct, more cohesive.



She didn't like it.



As was her habit, she reached across the bed, holding her companion close.



Not enough.  Not warm enough, not responsive, not caring.



He wasn't family.



She pushed her covers away, annoyed.



Blasto lay there, unmoving.



``Up,'' she said.



The hardware worked throughout his body bid him to move.



She stared at him, unfamiliar feelings warring inside her.  The dream was fresh in her mind and she couldn't banish it, just like she hadn't been able to banish it yesterday, or the day before, or the day before that.



It was just a little harder every day.



She felt a flare of anger, but pasted a smile on her face instead.  \emph{Think happy}.



\emph{Be good}, she thought, and the thought was too close to an idea in her dream.  It had the opposite effect, dashed her resolve to the wind.



She was left only with a mingled sense of unease and frustration.



\emph{No mind control?  My fanny!  }The darn woman in the suit \emph{had} put a mind-whammy on her!



It made her \emph{upset, }which was a terrible way to start the day.  Most days, she could cuddle with whoever was sleeping beside her.  Blasto wasn't so good at that.



It didn't help that Blasto had died a week ago.  A stroke, no doubt from stress, in the midst of a refrain of the Love Bugs theme song.  The only thing that let him move now were the control mechanisms she'd set up.



Not so good for snuggling.



Most days, if snuggling didn't quite cut it, Jack would keep her busy, give her something to do, and entertain her.  Always, his voice in her ear, always ushering her forwards, praising her for being a good girl, for her art, for her talent.  Others were interested.  Her family.



Now she was alone.



She left the closet that was her bedroom, with Blasto standing beside the fleshy mattress, and she approached the cases.



The third draft, still in a foetal state, nine of each.  She had a good feeling about it.  There were a few more brains to create, more personalities to research and draw up, but she felt fairly confident about her ability to piece it all together.



The only rub was the Bonesaws.  A whole row, empty.



They didn't need as long to gestate, but she had yet to begin figuring out how to create them.



She could have scanned her own brain and copied over the results, but the setup was awkward to manage, best done with a sleeping subject.  She could have set Blasto up to manage it, but\ldots that was tricky in its own way.



She wasn't used to feeling a lack of confidence.  The thing about \emph{art} was that one could create anything, could incorporate mistakes.  But art needed an audience and she had none here.



She'd set herself the task of having everything ready for when Jack and the others woke up, and now she felt she was unraveling, coming apart in the quiet and the solitude.



She stared at the seeds of the Bonesaws that hadn't grown and wondered if she really could look long enough to see the real her, to fabricate anything like herself.  Her test runs with the others had all worked.  They were close enough to feel familiar, even if little details were off.  Their personalities, their approaches, all would be close enough.  Here and there, she'd fixed things, corrected the most detrimental personality traits that had been turned against them and allowed them to be captured or killed.



Sighing, she turned away.  She took the time to dress in the clothes she'd bought, and then used the remote to teleport to Earth Bet.



``Our regular is back,'' the man at the counter said.  ``You get out a lot, with that home schooling.''



``Yeah,'' she said.  She folded her hands on the edge of the counter and rested her chin on them.  ``Your haircut looks good, Eli.''



``Thank you,'' he said.  He looked genuinely embarrassed.  She smiled a little at that.



``See any good movies lately?'' she asked.



``You like horror movies right?''



``Mm hmm.''



``The Darkness.  You'd like it, it comes from a good pedigree.  It's about a mafia-``



A woman entered the store, and Eli jumped as though he'd been caught doing something wrong.



``Can I- can I put up a sign in the window?'' the woman asked.



``I'd have to see it first,'' Eli responded.  ``Might have to ask my dad.  He owns the store, even if I run it.  If there's any question, it'd be his call.  He gets back this Monday.''



The woman's face was grave as she handed over the paper.



Eli took the time to read it.  ``I think everyone in town knows about this, Mrs. Hemston.''



``Can I put it up anyways?  If someone passes through and sees it-``



Eli shifted, uncomfortable.  ``I don't see any reason you couldn't.  My dad wouldn't say no.''



Without responding, Mrs. Hemston set about taping it to a spot at eye level on the back of the glass door.



She glanced at Bonesaw.  ``You shouldn't be out without a guardian.  Go home.''



``Yes ma'am,'' Bonesaw replied, smiling.



And then the woman was gone.



Bonesaw opened the door and held it open so she could see the sign.  A missing person sign, with a picture of a girl.  She let the door swing closed.



Eli hesitated.  ``Riley, I was thinking, if you wanted to come over and watch that movie\ldots''



``No.''



``No?  Why?''



``You know why,'' she said.  She walked down the aisle to grab some snacks.  Gummy candies, more Frooty Toots, some more milk.



``I wouldn't, you know I-``



``You'd be a gentleman, I'm sure,'' she replied.  The funny thing was, she \emph{was} sure.  She knew her monsters.



He struggled to recover.  ``I\ldots you're talking about the home schooling.  Strict parents?''



It was feeble.  She \emph{knew} it was feeble.



``Exactly,'' she responded, setting the stuff on the counter.  ``Sorry.''



``Eight ninety-five,'' was all he said.



He was hurt.  He'd recover.  She collected her things, gave him a small wave, and then made her way back.  She glanced at the woman who was making her way into the next store.



She stepped out of sight, then used the remote to exit back to the pocket realm.



She felt a growing sense of unease as she set the milk in the fridge and put the Frooty Toots on the counter with the candy.  Not an unease with what had happened with Eli.  That would resolve itself.  She'd see him in two or three days, and it would be awkward.  Then she'd see him after that, and things would be okay again.



No.  That wasn't what was resting heavily on her heart.



She called for Blasto and then entered one of the other closets.



Melanie, the girl's name was.



A week and a half ago, it had been so commonsense.  A solution to her problems.  The girl had been \emph{right there}.  So easy to approach.  A tranquilizer shot to the neck, calculated on the fly to fit with body weight and overall health.  Recalibrating the teleporting remote with the unconscious girl in the back lot had been a little riskier, but it was a quiet town.



Bonesaw had found herself busy enough that the girl could be left here, an IV in her neck, catheter and poop tube inserted.  Now that she had free time, she could handle the \emph{Winter} issue.



She needed a child soldier.  This was a way to make one.  To insert the wartime memories from Cranial's database into the girl, let it steep, then harvest the results.  The rest could be tweaked, rebalanced, fixed.



And there, again, that unease.



She couldn't think of her mother's face, only stitches.  Her father she hadn't even seen.  His face was a vague idea in her head, a few isolated features with nothing to bind them together.



Yet when she tried to visualize herself going ahead with it, it was Eli's face that intruded.  Disappointed, confused.



Eli and Mrs. Hemston both, now.



The girl was meat.  A tool, a collection of resources to be taken apart and put together in a different configuration, a machine.  Any number of things, but not a person.



But the people from the periphery of the girl's life\ldots they were harder to compartmentalize.  Distant.  They weren't at arm's reach to use as resources.



An emotional factor.



\emph{Darn it}, she thought.  She'd stopped talking to herself, after she'd gotten in the habit and weirded Eli out.



She turned her attention to the computer, crossing the room.  \emph{Need a distraction}.



Except it backfired.  She thought of the woman in the suit, and the statement.  Breadth and depth.



As things tended to do, a connection drew across her mind's eye.  All of the problems at hand, the challenges, dealing with the clones, figuring out how to program them.



The first batch had failed because they were too young, and the connection with the passenger had become too broad, consuming too much of their personality, leaving room for little growth as a human being.  Things were missing, other things bloated or exaggerated as the passenger needed.



Jack had a different kind of connection.  A \emph{deep} connection.  He was in alignment with the particular nature of his passenger.  The passengers naturally sought conflict, and Jack had fed that need from very early on, and he had sustained it for years.  The line between the two was so thin as to be impossible to mark, but Jack's personality remained his own.  Altered, but not subsumed.



And Bonesaw\ldots well, she was talented.  There was little doubt her passenger fed her a great amount of detail.



But what kind of connection was it?



\emph{Darn mind whammies!  Darn it, drat, gosh, golly fuck!}



She stared down at her hands, splayed and resting on either side of the keyboard.



What kind of connection was it?



Young age?  Check.  That had meant breadth for the others.



Fed by conflict?  Check.  Depth, if the single data point that was Jack was any indication.



\emph{How much of me is me}?



She stared at the backs of her hands.



\emph{What difference does it make?  }It wasn't a rhetorical question.  There \emph{was} a difference, it did matter in the grand scheme of things.  She just wasn't sure what that difference was, how it mattered.



She hadn't had to make many of her own decisions before.  Or, it was better to say, she hadn't had to make important ones.  There was a security in being with Jack, because it meant she didn't have to face this sort of thing.  One comment, and the question was decided.



She turned to look at Melanie.  The girl was her age.



Odd to think about.



The girl had seen her face.  She couldn't trust her ability to erase memories, not without test subjects, which was a new set of risks, a new set of problems.  It would only compound the problem she was trying to solve.



She wasn't used to thinking like this, considering ways to \emph{minimize} chaos.



Couldn't trust that she'd scrub the right memory.  It wasn't \emph{her} tinker tech.



Couldn't trust that she could \emph{overwrite} the memories either.  Inserting memories, yes, but the brain was a funny thing.  Again, it wasn't her tinker tech.



Going ahead would be safest.



She thought of Eli.  A friend.  Not family, like the Nine had become, but a friend.



She thought of the effect of the passenger on her personality.  Was the art hers or did it belong to \emph{it}?  Her sense of family among the other Nine, again, who did it belong to?



She bit a thumbnail, cut deep into the material with the special cutting materials she'd laced her incisors with, and then tore the end off in one swift motion.  The quick of her nail started bleeding.



The pain gave her clarity.



Maybe the family thing was the passenger's.  Maybe the art was too.



But Eli?  It wasn't perfect.  It wasn't normal.  But if the passenger had never made contact, and she'd still lived a life a little like the one she lived now, she could see herself being Eli's friend.



That in mind, she made her decision.



\sectionbreak



\strong{November 12th, 2012}



She shifted her weight from foot to foot.



A lot of time alone.  A lot of time to think.



Every decision now was made on a fulcrum.  Was she acting as \emph{Riley} or as \emph{Bonesaw}?



This\ldots it wasn't a \emph{hard} decision.  In a way, she'd imagined she'd always make it.  But it, like every other call, had to be carefully measured.



First menstruation, check.



Might as well get it over with.  She made notes on the computer.



Auto-hysterectomy.



Auto-masectomy.



Limb shortening.



Bone shaving.



Plastic surgery.



\emph{Bonesaw} would approve.  Maybe it would be better to be taller, to have more room for equipment.  Still, she could reverse the procedure.  It wouldn't be \emph{her} parts, but that wasn't such a problem.



But for \emph{Riley}, this was essential.  It was a matter of months before Jack woke.  She needed time to recover.  The clones were in a good state.  Only the Bonesaw vats were empty.  Each of the others had an adolescent or nearly-adult clone inside.  A month or two before the others woke from cryo-stasis, she'd start doing the surgeries, adding the augments, combining a handful of them together.



She laid out everything on the table next to her.  Scalpels, blood bags, IV drips, screwdrivers, wire, staple, cauterizing gun, hammer, stapler\ldots a mix and match.



She hefted the bonesaw and frowned a little.  The word had taken on a different meaning for her, in recent months.  It had stopped being \emph{her} name somewhere along the line, had become her passenger's.



Anesthetic?  No.  She needed optimal awareness of her own body.  Anything that dulled her senses would spoil that.



She had the ability to switch off pain at will.  She wouldn't use it.



No.  She wouldn't say she felt guilty about the things she'd done, but she recognized that she was broken, now.  She recognized that maybe she \emph{should}.



A part of her wished she could reach inside and find that carefree perspective, the \emph{innocence} she'd enjoyed.  Another part of her was glad.  Everything about herself was modifiable, reversible, pliable.  Pieces in the machine.  But this?  She wasn't sure she could alter it, nor that she wanted to.



This wouldn't be a penance.  That would suggest penitence.  But it'd be \emph{just}, as best as she could figure.



She started cutting.



\sectionbreak



\strong{January 24th, 2013}



``The sign's down,'' she commented.



``Riley!''  Eli looked startled.  He glanced back at his dad, who was stocking shelves.  ``It's been\ldots a really long time.  I was worried I said something.''



``No.  Went to live with my dad,'' she said.  The lie was smooth, effortless.  She didn't even feel bad.



``You're back?''



``Stopping by, like the first time you saw me.''



He nodded, still a little stunned.  ``Uh\ldots they found the girl dead in the woods.  Some dogs had chewed her up pretty badly.''



``Oh,'' she responded.  She'd practiced the look of concern in the mirror.  Even now, she didn't really feel \emph{guilt}, but nothing was reliable, like it once had been.  ``I stopped in to say goodbye, Eli.''



``Goodbye?''  He seemed more surprised than disappointed.



\emph{Maybe he already said goodbye to me}, she thought.  She didn't feel hurt.  Growing up with the Slaughterhouse Nine had numbed her in many respects.  It made sense, little more.



``I wanted to give you a gift,'' she said.  ``As thanks for the movie advice, and the conversation over the past while.  You helped me, gave me a friend when I needed one.''



He frowned.  ``After your parent's divorce, you mean.''



``Yes.''  Another easy lie.



``I get that,'' he said.  He looked at the card.  ``Can I open it?''



``No.  There's a date on it.  Wait, then read it on the date in question.  Break that rule and I'll be \emph{mad}, understand?''



``I understand,'' he responded.  He looked down at the envelope.  ``My birthday.''



``Yeah.  And I don't think you \emph{do }understand,'' she said, ``But that's okay.  Just don't break the rule, and don't lose the letter.''



``Okay,'' he said.  ``Um.  I would've gotten you something, but\ldots oh.''



He rummaged in his bag, then handed her a video tape.



``I\ldots I rented it, but I'll pay the fee to replace it.  One of my favorites from the last year.''



A horror movie.  A child werewolf?



A child monster.



She glanced at him, but there was nothing in his expression.  She'd become exceptionally good at reading people, and\ldots no.  He had no idea how ironic the gift was.



``Thank you,'' she said, holding it to her stomach.  ``It's probably okay if we just say hi and bye like usual, isn't it?  Fits?''



``You look different,'' he blurted out the words, a non-sequitur.



She'd hoped the winter clothes would hide any of the reversions she'd made.



``You look good,'' he added.



``Be \emph{fucking} good, Eli,'' she retorted, staring at him.



Before, he might have protested, feigned confusion.  He'd changed, much as she had.



Now, he only nodded a little.  ``I will.''



\sectionbreak



\strong{May 25th, 2013}



She sat with her feet propped up on the table, a bowl of Frooty Toots on her stomach, as the alarm went off.



She felt a momentary sadness.  She tapped her pinky with her thumb twice, and the embedded magnets noted the signal.  She'd recorded her own brain activity and movements when contemplating the Bonesaw clones, and it was this that she drew on, manipulating her own body much as she had manipulated Blasto's.



Her body language wasn't her own.  Her smile, the way she walked, the gestures, all were fine tuned to match the Bonesaw of before.



Her height, too, had changed.  She'd cut her hair to match, had downgraded her body so the last year and a half of development had never happened.



It was the burning of a bridge, in a way.  It would retard her growth in the future, and that would arouse suspicion.



In a way, she couldn't carry on her relationship with the Nine.  There would be too many tells, no time to herself to make changes in secret.



The individual cases opened, and slowly but surely, the members of the current Slaughterhouse Nine stepped out.  Jack, Hookwolf, Skinslip, Night Hag.



She could see the conscious effort on Jack's part to maintain his composure.  He was barely able to stand.



His eyes fixed on her.



Somehow, she \emph{knew}.  She knew he knew.  But that was no surprise.



All she \emph{really} needed was reasonable doubt.  He would harbor suspicions, and he would pull something on her.  \emph{Later}.



In the meantime, she'd have options.



``You're awake,'' he commented.



``And you're nude,'' she said, covering her eyes.  ``Where are your\emph{ manners?''}



Like riding a bike.  Back to her old self.  Playing the role.



``I'll remedy that in an instant.  \emph{Cereal}?''



``Made it myself.  Took me a whole \emph{three hours} to get it right.  Felt like keeping busy.''



``And the milk?''



``Made it myself,'' she responded.  She grinned, and the device took over, gave it that width, that guilelessness she couldn't manage on her own.



``I won't ask.  My clothes?''



She pointed him in the direction of the closet where she'd placed all of the roughspun uniforms, alongside the clothes Jack and the others had removed before stepping into the cryostasis chambers.



He took a step, then stumbled.



``I'm\ldots not as coordinated as I should be,'' he said.



``Seems there's trouble with the recovery phase,'' Riley said.  ``Be a month or two before you're on your feet.''



``We have a schedule.''



``I know.  But I can't fix this.  Not my stuff.''



He stared at her, brushed ice-crusted hair away from his face.



But she wasn't lying.  There was no falsehood to pick out.



``You could have woken us sooner.''



``Nope, nope,'' she said.  ``Would've mucked up the scheduling.''



Still, that penetrating stare.  This was the make or break moment.



``Well,'' Jack said, smiling, ``Unavoidable.  We'll have to make it extra special.''



``Triple special,'' she answered.  ``Things have been \emph{interesting} while we've been gone.''



``Interesting?''



``I'll show you later.''



``And the clones?''



``I was waiting for you to wake up before we greeted them.''



``Good,'' Jack said.  ``Excellent.''



She smiled wide as he turned, covering his bare rear end on his way to the closet, even as she felt coldness in her heart.



Hookwolf, for his part, only drew blades around his body, forming into a giant metal form.  She wondered if he looked a little introspective, before his head was covered in the mass of shifting, \emph{skirring} hooks and needles.



She chewed on her cereal, and watched more of her movie.



She \emph{did} like it, after all.  Eli had been right.



She smiled, hiding the sense of loss as she deleted it from the system and cleaned up the evidence.



One by one, the recently unfrozen members of the Nine rejoined them, dressed in their outfits and costumes.



Jack gestured, and she hit the key on the keyboard.  \emph{Lights.}



Spotlights went on beneath each of the glass chambers.



\emph{Drain}.



The fluids poured out, draining into the openings in the floor.  Blurry figures became more distinct, marred only by the residual droplets clinging to the interior of each chamber.



``You didn't do yours,'' Jack commented.



``Didn't work out.''



``I see,'' he said.



Every line of dialogue felt like a nail in the coffin.



But that coffin wasn't a concern today, or even tomorrow.



For now, Jack needed her.  For now, she had options.



She smiled, wide, with a glee she didn't feel.



The woman in the suit had options.  She would come to Riley and claim the remote.



Countless enemies would be mustering their forces, ready to deal with this.



Eli had the letter.  He'd find a plane ticket inside, along with an urging to leave and stay gone.  To drive the point home, she'd revealed her identity.



Yet Riley still felt a moment's doubt.



Some rose from their knees.  Others had managed to remain standing from the moments the fluid left the chambers.  As they roused, powers flickered into action.



Siberians flickered into being near the Mantons.  Six like the daughter, three more like Manton himself, all in black and white.



Chuckles, tall, fat, with arms that zig-zagged, her own addition.  Thirty-one elbows, and arms that dragged behind them as they moved.  Here and there, one of them would twitch, a tic.  The clown makeup was a series of scars, tattooed on.  One activated his speedster abilities experimentally, crossing the room in a flash.



Nostalgic, in a way.  Chuckles had been around when she'd joined.



Murder Rat.  Not stapled together as the original had been.  She'd taken the time to do it well.  When membership had been down, Bonesaw had made Murder Rat as a \emph{created} addition to the Slaughterhouse Nine.  She'd passed the tests, but degradation in mental and physical faculties over time had seen to her demotion.



Winter, white-haired, with white irises edged in black, nude, her eyes peering.  \emph{Madeline's eyes}, Riley thought.  Winter would need guns, of course.



Crimson, Winter's brief-lived lover.  Riley had taken the time to program their relationship into them.  Crimson had been one of the first members in the group, Winter one of the more recent ones to die.  Winter had been followed by Hatchet Face -there he was, over there, nine of them- and Hatchet Face had been followed by Cherish.



Nine Cherishes, gathering in a huddle.  She'd forgotten to give them the tattoos.  It didn't matter.  A glance suggested they were discussing different ways to do their hair.



The smile on her own face was so wide it \emph{hurt, }but it wasn't her smile.



King, tall and blond, unabashed in his nudity.  All nine Kings were broad-shouldered, each half a foot taller than Jack.



Their interaction would be an interesting one.  She'd wondered if she should program King with the knowledge that Jack had been the one to kill him, reconsidered.



Oh, and there were others.  Some were harder to recognize.  Nine Alan Grammes, who lacked his armor.  Nine \emph{Neds}, narrow shouldered and only five and a half feet tall.  When the others had done some damage and given him a chance to regenerate, he'd resemble his true self a little better.  He'd be \emph{Crawler}.



``And the last one?''  Jack pointed at the remaining chamber.



She hit a button, and for a moment, her expression slipped.  She closed her eyes, a brief moment too long, as nutrient soup drained out of the chamber and the glass lowered.



But nobody was looking at \emph{her}.



The boy stepped out, and there was no sign of any difficulty.  He didn't struggle as others had, nor have trouble finding his feet.  He was prepubescent, to look at him, older than ten but younger than fourteen.  His hair was neatly parted, and he wore a private school uniform, complete with glossy black shoes.  Dry.



\emph{Even though he was naked in the tube}.



Then again, that was sort of his thing.  One of them, anyways.



Visually, the most notable part of him was the effect that surrounded him.  He was monochrome, all grays and whites and blacks, with spots of light and shadow flickering around him.  Here and there, \emph{he} flickered, a double image momentarily overlapping him, ghostly, looking in a different direction.



As far as parahuman powers went, his was as unfair as they got.



``Jack,'' Gray Boy said.  His voice was high, clear as a bell.



``Nicholas.''



Jack extended a hand and Nicholas shook it.



Riley felt her stomach sink.



It would be like Gray Boy to use his power and take out someone in the room, just because he \emph{could}.  Jack had only wanted one, and the unspoken reality was that he only wanted one because he could only \emph{control} one.



If he wasn't going after Jack, then\ldots she was the only other person in the room without clones surrounding her.



He approached her, his expression placid.



For a brief moment, she felt stark fear.



It was perhaps her salvation that the fear was buried under the expressions that her system pasted on her face.  The false smile that spread across her face was the push she needed to hop down from her seat, approaching him.  She leaned in close to kiss him on the cheeks, her hands on his shoulders, one leg cocking upward like she'd seen women in older films doing.



``Little brother,'' she murmured.



``Bonesaw,'' he said, voicing a name she hadn't programmed into him.  His hand found hers, and he held it.  She felt a chill.  ``We'll be inseparable, I think.''



``Inseparable,'' she answered, smiling falsely.



The others from rows further down in the chamber slowly approached.  She watched Jack taking it all in.  Two hundred and seventy-five in all.  Two hundred and seventy regulars, five special makes.  Snowmann, Nighty Night, Laughjob, Tyrant, Spawner.



The names had never been a strength of hers.



\emph{I've given you everything you want}, she thought.  \emph{Now we see who comes out ahead.  Succeed, and Bonesaw comes to the fore.  Fail, and Riley wins}.



She wanted Riley to win, but that wasn't as simple as making a decision.  She had to bury her life with the Nine.  Bury Jack, and see him defeated.



Gray Boy squeezed her hand.  She would have jumped, if her body language wasn't in the system's control.  She looked at him, and he winked.



Her expression hadn't wavered, she hadn't allowed herself the slightest tell, but somehow he fell in the same category as Jack.



He \emph{knew}.



Staring out at the gathered crowd, Jack seemed to reach a conclusion.  He glanced at her, as Gray Boy was doing.



``Good,'' he said.





