





Creepy crawlies riddled the building's interior, and I hadn't even used my powers to bring them here.



No power meant the building was dark.  The city, and consequently the building, were flooded, which meant it was moist.  With exceptions for some of the luckier areas, pretty much every service was suspended, which meant no mail and no trash pickup.  Trash bags were accumulating anywhere that people lived, here included, and when they had run out of trash bags, people had started littering, throwing their trash out the windows or leaving it in hallways instead.  To top it off, the weather was getting warmer.



For bugs, all of these converging details made the city into a paradise.



I walked in the lead of the group, with Imp a step behind me and to my right.  The two of us held flashlights, but Imp was barely paying attention to hers.  She held a knife much like mine, and she dragged the point against the wall as we walked down the hallway, carving a groove into the paint.  Her flashlight spent more time pointed at her feet than in front of us, leaving me the burden of lighting our way.



I stopped, turned the flashlight on an open apartment door.  ``Here, maybe?''



Grue grunted, adjusted the position of the unconscious body he had draped over one shoulder, ``Scout it.''



Bitch nodded, letting Angelica off the chain, pointing at the door.  Of the four dogs she had with her, only Angelica was still under the influence of her power, standing three times her usual size.  Despite the invigorating effects of Bitch's attentions, the dog moved slowly as she loped into the apartment.  It was painful to look at her – she was moving as though she were ten years older than she was.



The other dogs pulled at their chains, wanting to follow.  Bitch made angry clucking noises, then ordered them to sit.  They were slow to obey, but I think something about the look in Bitch's eyes told them they'd better listen.  One of them reared back as I sent more bugs into the interior to investigate.



Bitch had been short-tempered lately.  The loss of two of the dogs she was closest to?  It played a large part in that.  She'd lost eight dogs in total, and Angelica had only lived because she had been too hurt to be brought along.  Problem was, Angelica wasn't recovering from those injuries, and from what I gathered, she might not ever recover completely.  Bitch was forced to rely on a single crippled, obedient dog and three dogs that were in the peak of health, but impatient and untrained.



Of course, I couldn't deny that a big part of her attitude was me and the fact that I was here.



Angelica returned to the doorway, looked up at her owner, and then returned to the apartment.



``No problems,'' Bitch spoke, translating Angelica's body language for everyone present.  Grue looked at me, and I nodded confirmation.



I led the way inside, using my flashlight to scan the area.



The apartment had been ransacked, but it wasn't the kind of ransacking that suggested the looters had gotten to it.  No, it was the very thorough removal of everything valuable that could be carried away by a family of three or four.  There were two bedrooms, a bathroom, and a kitchen with room for a small table and accompanying chairs.  There was a smaller bed in one room and a king sized bed in the other.  Dresser drawers, cabinets and bedside tables were all open, clothes strewn around the rooms.  The occupants had left in a hurry, and I was guessing they probably hadn't expected to come back or find much of their stuff here when they did.



Tattletale grunted as she dropped one box beside the couch, where it landed on something with a crunch. ``City's trying to restore order one area at a time.  May be doing more harm than good.  This building's been declared uninhabitable, which isn't exactly doing anyone any favors, because most places in the city are just as bad or worse, and a lot of people don't have anywhere else to go.  Anyways, they're kicking everyone out, trying to clean up as best they can, get rid of that trash, do what they can about the infestation of rats and bugs.  Might still be a few people around, but I doubt anyone's going to be poking around enough to find us before eleven or so tomorrow morning.''



``Then we have time to do what we need to do,'' Grue spoke.  He used one foot to drag one of the dining room chairs out from beneath the table, placing it in the center of the kitchen.  I hurried to his side to hold the seat in place as he hefted the limp body from over his shoulder and set it down.  Shadow Stalker nearly tipped over, but together we caught her and leaned her back.  Her head lolled.



Regent put down a second, smaller box next to the one Tattletale had brought.  I switched positions with Tattletale – she began searching Shadow Stalker, removing crossbows, cartridges of ammunition and two small knives.  She found a phone with a touch screen, then reached beneath the unconscious girl's hood to pluck a wireless earbud from the girl's ear.  After rubbing it on Shadow Stalker's cloak to clean it, she put it in her own ear and started fiddling with the smart phone.  After a few seconds she pronounced, ``GPS hasn't been activated.  They probably won't turn it on to look for her until she fails to return from patrol.''



``Can you stop them from activating it?''  Grue asked.  ``Or maybe we could have Skitter's bugs or a dog carry that piece somewhere else?''



Tattletale shook her head, ``I can turn it off.  Give me a minute.''



Regent and I had already started hauling extension cords out of the box Regent had been carrying, untangling them and feeding them over to Grue.  He began winding a cord around our captive, starting with loops around her wrists and arms, going up her arms to her chest, then back down to bind her body to the chair.  We handed him the next cord, and he did much the same thing with Shadow Stalker's legs.  As he worked the bindings up her extremities, he kept his index and middle fingers on her, wrapping the cord over top of them.  When he was done with the loops at one spot, he moved his hand up further, then repeated the process.



``Copping a feel, Grue?'' Imp mocked, as she let herself half-spin and collapse lengthwise on the couch.



``Making sure it isn't tight enough to cut off her circulation.''



``Ah.  You an expert on that stuff?  I didn't take you for a bondage freak,'' she stretched.



He sighed, ``Just get the generator.''



``I just lay down.''



``So stand up and \emph{then} get the generator,'' he ordered.



She made a show of slowly standing and, with exaggerated motions, dragging herself over to the box Tattletale had brought.  She retrieved a black plastic portable generator that wasn't much bigger than a microwave oven.  She acted like it was ten times heavier than it was as she hauled it over toward the spot where Sophia sat.



Grue, for his part, ignored her.



Once the wires were in place, he used duct tape to secure them, then he got two more chairs, laid them on their sides and taped them to her chair.  He was almost done when Imp finally concluded her charade with the portable generator.  The LEDs at the ends of the extension cords lit up as we plugged each cord in to the generator, glowing a dim orange.  Grue stood, then pushed the refrigerator away from the wall so he could unplug it and plug the appliance into the generator.  I couldn't be sure if it was to ensure a steady current  through the wire or because he wanted a working fridge.



I'd finished unpacking the wires, so I picked up the empty box and entered the living room to put one box inside the other to minimize the mess.



Bitch had claimed the sofa for herself, reclining with two dogs up beside her.  She was rubbing her forearms, which were probably strained from controlling the more unruly dogs with the chains.  She glared up at me, and there was something ugly in her expression.



I couldn't blame her for being angry.  Her dogs, some of her closest friends in the world, had died because she had been saving me, only for her to find out shortly afterward that I had been a traitor.  Maybe saving me hadn't been her primary motivation, but it seemed she'd used the past week and an unhealthy dose of simmering anger to revise her perception of things so I was to blame for what had happened.  It wasn't getting better, either.  She seemed to get angrier with every hour spent in my company, and I was worried I'd have to face the brunt of it very soon.



``She's awake,'' Tattletale called out.  I hurried to the kitchen, leaving Bitch where she was.



Our captive hadn't budged an inch.



``She's sitting there, pretending to sleep in the hopes that we'll say something.  It would be clever, might even work, if I wasn't here,'' Tattletale said, with a bit of a wry tone.



Shadow Stalker's head rose and swiveled as she surveyed the full extent of her bindings.  Then she glanced at us.



After a long pause, she spoke, ``Electrical cords.''



``Strongly advise you to avoid using your power to pass through them,'' Tattletale answered, ``And in case you're thinking of dropping straight down through the floor, don't.  We've got extra lying under the chair.''



The heroine leaned hard to one side, looked down.  ``Hm.''



``You'll be a little groggy,'' Tattletale grabbed the last remaining chair from beside the kitchen table to sit down opposite the vigilante `heroine'.  ``The fight took a lot out of you, and we tased you, \emph{and} I took the liberty of sticking you with one of your own tranquilizer bolts.''



``You don't hold back,'' Shadow Stalker commented, seemingly unfazed by her circumstances.  She tested the strength of her bonds, experimentally.



``Says the person who tried to slit my teammate's throat,'' Regent spoke.



Shadow Stalker looked at me, the eyes behind her mask moving to my throat.  ``Tough costume.''



\emph{She doesn't even deny it.  }\emph{I can't believe I've gone to high school with this lunatic}.  I resisted the urge to respond, shrugged instead.  Too easy to get into an argument, too easy to let something slip and reveal who I was.



``Well, you fuckers got me,'' she cocked her head to one side, ``What's next?''



We all turned to look at Regent.  Regent, in turn, gave Shadow Stalker a serious look.  He ran his fingers through his dark hair.  Tattletale stood from the chair, and Regent sat, putting himself four feet away from the heroine.  His mask was a plain white, a half-smile perpetually frozen on the smooth, unadorned face.



Her eyes went wide behind the eyeholes of her mask, and she pulled hard against her bonds, ``No!  \emph{Fuck!}  Have you seen his files?  You don't know--''



``We have an idea,'' Tattletale interrupted.



``Fuck you!''  Shadow Stalker shouted.



``Guys, do me a favor?'' Regent asked, not taking his eyes off Shadow Stalker.  He smacked his scepter into the palm of one hand, ``Gag her, then give us some privacy?''



``You sure?'' Grue asked, as Tattletale moved over to Sophia's side, bent down to get some excess cord, and lifted up her mask just enough to wind the cord into her mouth.  The duct tape made a tearing noise as she freed a length from the roll.  I could still make out the swearing on Shadow Stalker's part as she tugged at her bonds and rocked her seat.  The setup Grue had created by duct taping the other two chairs to her helped ensure she couldn't throw herself to the ground and maybe break the chair in the process.



``I'm cool.''  Regent shifted the position of his stool a half-foot to his left, so he could lean back against the corner of the refrigerator.  He brought one of his feet up onto the seat of the stool and rested his chin on his knee.



``Just as long as you're sure,'' Grue spoke.  ``How long?''



Regent glanced at Grue, then looked to Shadow Stalker, ``Depends on her.  Could be fifteen minutes, could be three hours.''



Shadow Stalker grunted, long and loud.



Grue began ushering us out of the room, and we obeyed, except for Imp, who seemed to need a little bit of an extra nudge – Grue blocked her view of Regent and our captive with his body and put a hand on her shoulder to push her toward the door.  Following, I cast a backward look over my shoulder, saw Shadow Stalker's arm twitch.  She winced, mumbled a swear word around her gag.



Grue shut the kitchen door behind us, and for a moment, all was dark, quiet and still.



Bitch and her dogs were all lying together on and around the couch, Bitch's hand on Angelica's head, where the dog lay just below her.  Only Angelica's eye was open – Bitch and the other three dogs had their eyes closed.  Angelica's excess flesh had been shed and deposited on the floor as she shrunk down to her natural size.  It looked like Bitch had kicked most of it one corner of the living room; blood and other fluids streaked the carpet between the base of the couch and the corner.



``Can we watch TV?'' Imp asked Grue, ``We could get one of the extension cords and--''



``No.''



``Or plug in one of the lamps so we can--''



``No,'' he repeated.  ``We're here for another few hours.  We do nothing that could draw attention.  That includes having lights, flickering or otherwise, shining through the window of an apartment that's \emph{supposed to have no power}.''



``What the fuck am I supposed to do?''



``Sleep,'' he glanced at Bitch, who was trying to do just that, ``While the rest of us stand watch.  Or go looking for a candle or flashlight and read somewhere the light won't show through a window.''



``Fuck reading.  We could find a movie and watch--''



``No movies, I just told you why we can't turn on the TV.  Why would a movie be any better?''



``We could cover one of the windows!''



``I want everyone keeping an ear out for trouble.  You agreed to follow my orders, didn't you?  \emph{No TV}, \emph{no lights}.''



They glared at one another, Imp's chin defiantly raised so she could meet Grue's `eyes' – the dark sockets of his skull-faced helmet.



``One of the people who lived here was a teenager, a little younger than you, Imp,'' Tattletale cut in, ``Go find the bedroom, see if there's anything interesting.  Anything left behind will probably get stolen before the family gets back, so you could keep some stuff for yourself, if you find anything good.''



``Yes!'' Imp spun on her heel and strode off to the other end of the apartment.  Bitch opened her eyes and furrowed her brow in irritation at Imp's outcry, or maybe at the recent argument, but she just shut her eyes and made a deliberate attempt at returning to sleep.



Grue waited until Imp disappeared from sight before groaning, ``It's tiring, dealing with her.''



``All of us irritated each other when we first joined the team.  Give it time.  We'll find a rhythm.'' Tattletale reassured him.



Grue turned his head my way, but he didn't say anything.  I wondered if he had been about to say I was the exception, then changed his mind.



Instead, he spoke, ``I'm going to lie down for a bit in the master bedroom.  Tattletale, Skitter, you keep an eye on things.  Wake me when you need a relief.''



``Sure thing, boss,'' Tattletale answered him.  I couldn't bring myself to reply, and stayed quiet instead.



As Grue was leaving, Shadow Stalker screamed from the kitchen, a strangled, muffled noise.  Grue paused, waited a moment, and then continued in the direction Imp had gone, opening and closing the door at the end of the short hallway.



I hugged my arms against my body.  Glancing toward the balcony showed that none of the windows were broken or open.  It wasn't because I was cold.



``You okay with this?'' Tattletale asked.



``All-in,'' was all I could say.



She smiled a little, almost apologetic. ``All-in.''



We were doing this to Sophia, I told myself.  The same girl who had abused, insulted and tormented me almost every school day since I'd started high school.  She'd punched, kicked and shoved me.  Had ruined my belongings, insulted me, thrown food at me, humiliated me, and had goaded others into doing much the same things.  She was the one who had pushed me to that do-or-die point where my powers manifested.  If that wasn't enough, she had tried to kill me less than an hour ago, not because I was a criminal that deserved the death penalty, but because I had seen her unmasked.  I was \emph{inconvenient}.



And with all that in mind, I couldn't be sure that she deserved this.



Tattletale got her MP3 player and put an earbud in the ear that didn't have Sophia's device in it.  The other earbud dangled from the cord, faint music playing from it.  Grabbing a blanket from the arm of the couch, she curled up in one of the armchairs.



I took her cue, pushing one chair across the carpet so it was by the sliding glass door leading to the balcony.  I didn't settle in right away.  First, I exercised my power.



There were definitely enough bugs in the building for me to use.  I found the spiders in the building, and set them to preparing webs, stringing strands across every doorway, hallway and stairwell for every floor in the building.  I directed buzzing houseflies and mosquitoes into every apartment, including the one we were in, and placed at least one bug on every person I found still inside the building – a trio of unwashed men in the basement, among the storage area where residents kept the stuff they couldn't have in their apartments, a pair of teenagers that lay on the roof, holding hands, an older man near the top floor, alone, and one family of five on the second floor.



After a moment's consideration, I set spiders to stringing webs around the balconies as well.  When capes were in the cards, I couldn't afford to ignore the possibility of grappling hooks, rappelling, teleportation or flight.  The spiders would sense any movement of the webs, and I could sense what the spiders did, in turn.



I found a book on a shelf that looked readable, then sat down sideways in the chair, so my back was against one armrest and my legs hung over the other, the kitchen door in front of me, the balcony behind.  There were no lights in the apartment or out on the street, but the heavy clouds weren't blocking the moonlight for the time being, which afforded me the opportunity to read, looking up after every page or two to double-check that things were quiet and still.  It might have been peaceful, if not for Shadow Stalker's occasional grunt or scream from the direction of the kitchen.  On occasion, she went into her shadow state for a fraction of a second, then reverted back before the wires passed through her.  Regent hadn't called out, so I assumed all was well.



Bitch's bulldog, Bentley, was lying on the couch with his head nestled in Bitch's armpit.  I was on chapter three of my book when he began snoring, surprising me with how steady and loud the noise was.  Sirius, the lab I'd met on a prior occasion, lay between Bitch's legs, his head lying across her belt buckle.  A setter was curled up at the base of the sofa with Angelica – I couldn't remember its name.



Bitch looked so peaceful, here.  It was strange seeing her relax and rest so easily when, day-to-day, even before recent events, she seemed to be on edge to a degree that would drive most people to insanity.  It wasn't aggression or anxiety, exactly, but some combination of the two.



Tattletale was playing some game on her mp3 player, I saw.  The mosquitoes I'd placed discreetly on Brian's back told me he was turning over constantly.  He was as restless and agitated in relaxation as Bitch was when awake.



Imp, I could sense, was taking apart the teenager's room, finding CDs and DVDs and holding them up by the window, maybe to see them in the light, as I was with my book.  I hadn't known her to rest in the three days I'd known her.  I could almost believe she was one of the capes that didn't need to sleep, but the theory would have felt a lot more tidy if I could connect it better to one of her powers.



I turned my attention back to my book, looked up again when I heard a bang from the kitchen, a grunt and a scream.  The bugs I'd placed on Regent didn't show anything amiss, but I couldn't really get anything from the contact with Shadow Stalker.  She was violently flickering in and out of her shadow state, now, and the slow speed with which she was returning to normal seemed to suggest she was fighting the urge to use her power.  Regent was standing, but he hadn't called for help, so I started to read again.



When I'd read the same page four more times and realized I hadn't actually taken in any information, I dog-eared the page and closed my book.  I focused on each person in the building in turn, followed by a double checking of the spider webs, the others here in the apartment-



I stopped short.  Regent was sitting, unmoving, and in the last ten seconds or so, Shadow Stalker had disappeared from the chair.



``Fuck!'' I shouted, standing.  \emph{How?}



Bitch climbed up off the couch, and Tattletale stood, looking to me, eyes wide.



When I realized \emph{why} her eyes were wide, I let the bugs flow from beneath the panels of my costume.  I knew in an instant that Shadow Stalker was behind me.



Deftly, she grasped my wrist, knocked me to the ground, and then pointed her crossbow straight at my eye, the arrowhead clinking against the lens of my mask.  Which definitely wasn't bulletproof or arrowproof.



For several long seconds, we remained there, unmoving.  Brian and Imp appeared in my peripheral vision, but they stopped when they saw Shadow Stalker.



Shadow Stalker started laughing, then stood, holstering her crossbow.  I felt Regent stand in the other room.  When the kitchen door opened, he was laughing as well – the exact same cadence as Shadow Stalker.



He ran his fingers through his hair, and Shadow Stalker moved one hand, as if to do the same thing, but the hood she wore stopped her.  She stepped away, and her movement seemed uncannily out of character; maybe a bit of a slouch, a bit of swagger, that hadn't been there before.  Her eyes met mine.



``Totally got you, Dork,'' she chuckled.





