





\strong{3 Days Ago}



I drew in a deep breath, then exhaled, long and slow.



``I got your back,'' Lisa told me.  I nodded.



With a push, the door swung wide open.



The inside of the building didn't match the exterior.  It was situated in one of the low-lying areas of the Docks, where the flooding had yet to fully dissipate.  The buildings around here were in such bad shape that nobody was willing to use them for shelter or venture inside to take things.  On the inside, however, the place was reinforced with girders and beams.  Pieces of sheet metal sat between the thick metal shafts and the exterior wall, with holes cut to accommodate the windows.  Handles on the metal shutters suggested that the plywood could be moved aside in a pinch.  At ground level, there were stacked sandbags of a slightly different make from the usual, with plastic stapled over each pile.



The place hadn't yet been organized.  A pair of beds sat in one corner, surrounded by assorted pieces of furniture.  The building's interior was dry, crisp, and brightly lit.  It might have appeared sterile, if not for the spray paint on much of the sheet metal, and the tracks of dried mud on the ground near the door.



Our arrival was met by the furious barking of a half-dozen dogs.  A set of gates ringing the front door stopped them from attacking us.  Brian was sitting on the far end of the room, beside Aisha.  He wore his regular sparring uniform, and Aisha wore much the same thing, though she was wearing shorts instead of yoga pants.



\emph{His little sister? Here}?



Alec was sitting cross-legged on a pile of furniture, a bowl of colorful cereal balanced on one knee.  A long cut ran from just beneath his ear to his shoulder, beneath his shirt.  He was watching a TV that was plugged into an extension cord that hung from the ceiling.  He'd turned my way at the barking of the dogs, and I almost missed him uttering the words, \emph{``You gotta be kidding.''}



One of the dogs apparently recognized me, because it stopped at the gate and wagged its tail.  A part of me took that as a good sign.  Then Bitch appeared, immediately wheeling on me, water flying from her damp hair.  She'd probably just come from the shower – she wore loose fitting army pants and a black tank top that had darker spots where beads of water had soaked into it.  A towel hung around her shoulders.  As she saw me, emotion hardened the lines of her face.  Her hands clenched as she strode toward me.  I saw the aggression in her body language, squeezed my eyes shut and tried to relax.  I remembered what Brian had said during our sparring, about how tensing up would only make you more vulnerable.



If that was true, I was \emph{really} glad I hadn't tensed up.  She was sturdily built and she didn't hold back in the slightest.  She kicked down the dog gate, and an instant later, her fist connected with my cheekbone to send me sprawling to the ground, my tailbone absorbing most of the impact.  I'd been knocked around by Lung, Glory Girl, Bakuda and even Leviathan.  Some of those guys hit \emph{magnitudes} harder than Bitch did, but it still hurt like hell.



It spoke volumes that while Lisa stepped forward so she could defend me, Grue and Alec didn't.  The dogs tentatively passed through the open gate, but hung back in deference to their master.



``I-'' I broke off mid-sentence – opening my mouth to speak had caused the pain in the right side of my face to come to bear, full force.  ``I deserved that.''



Bitch delivered a swift kick to my shoulder, making me grunt and fall flat onto my back.  ``Deserved that too.''



``Point made,'' Lisa told her. ``Stop.''



``Fuck you,'' Bitch snarled.  She pointed at Brian.  ``It's irritating enough that \emph{he} wants to start giving orders and calling himself our leader, I'm not putting up with it from you, too.  I do what I want, and what I \emph{want} is to beat her face in.''



Bitch turned, strode to the pile of furniture, and then lifted one of the loose shelves that had been removed from the bookcase.  It was  a piece of wood chipboard about three feet long and a foot deep.  Lisa moved to put herself between Bitch and me and stave off Bitch's attack.  She turned to Brian, ``Hey, a little help, here?''



Brian frowned, ``Why did you bring her here?''



``To talk,'' Lisa said.  When Bitch tried to move around to her left, Lisa shifted her position to stay in her way.  I sat up, used my legs and hands to put some distance between Bitch and I.



``She was going to fuck us over!'' Bitch shouted.



I shook my head, but Bitch and Lisa's movements left me unsure if Brian had seen.  I called out, ``No!  I wasn't!''



Brian stepped forward and put a hand on Bitch's arm.  She scowled but lowered her improvised weapon.



He leveled a serious look at me, ``Lisa said you were, and when it comes down to the two of you, I'm going to choose her.  What Armsmaster said made too much sense, and a few of the little things about you suddenly made a lot of sense.''



``No, I- I mean, I \emph{was }going to betray you-''



``I'm going to fucking kick her teeth in!'' Bitch shouted.



``Past tense!'' I raised my voice, ``I changed my mind!''



Bitch made a deeper noise, low in her throat.  Aisha and Alec approached, which contributed to the loose half-circle of people and animals  around Lisa and me.  Tension hung heavy in the air.



``You changed your mind,'' Brian didn't sound as though he believed me.



``Dealing with Armsmaster?  Realizing what an asshole he was?  It was kind of a wake up call.  I'd already begun to think of you guys as my friends.  And what we were doing, it wasn't so bad.  Most of our fights were against Lung's gang\ldots''



Barring Lisa and Aisha, every set of eyes on me was glaring.  I climbed to my feet, flinched a little as Bitch shifted position, fearing another attack.  My cheek was radiating pain, like someone was driving a nail into it.  My shoulder didn't hurt half as much, but it wasn't exactly fun, either.



``I-I changed my mind after we raided the fundraiser and talked to Coil.  I went home, and when I started thinking about sending that email to the Protectorate, I realized I couldn't.  It would have meant explaining things to my dad and leaving you guys.  I couldn't do either.''



``That wasn't all that long ago, and it sounds pretty thin to me.''



I raised my arms, in a bit of a helpless gesture, then let them flop back to my sides.  ``It's the truth.  I'm not good at this, at talking to people or convincing them.  All I can do is tell you how things were from my perspective and hope you'll see I'm sincere.''



He folded his arms, ``Is that all you came to say?''



I drew in a deep breath, then sighed, ``And I'd like to be back on the team if you'll have me.  Please.''



His eyebrows rose, ``I seem to recall you leaving in a huff after our last conversation with Coil.  What's changed?''



``You have to understand, I was angry at myself as much\ldots \emph{more} than I was angry at you guys.  For letting that thing with the little girl happen, for not connecting the dots.  But I've thought about it, talked to Lisa, and I'm open to talking about it if you're willing.''



``And why should we believe you, in all this?'' he challenged me.



``I can vouch-'' Lisa started to speak.



``Taylor can answer for herself,'' Brian cut her off.



I floundered for an answer.  I got the distinct impression that they wouldn't be satisfied if I couldn't provide one.  A knot of ugly emotions gathered in my stomach, building as I felt the condemnation of these people I'd been so close to, not so long ago.



Realizing that much gave me an idea.  It wasn't much, though.



I turned to Brian, ``You remember when we were on the way to your apartment, what happened?''



``Which?  That thing with the bully, or-''



``After that.  The, um, awkward conversation.''



``Hey, dork,'' Alec cut in, ``He's not the only one you have to convince.  You can't omit details and leave us in the dark here.''



``Yeah!'' Aisha added.  Brian gave her an annoyed look.



I looked at him, then looked down at the ground, feeling heat spread across my face.  The flush in my cheeks made the side of my face throb.  I hated feeling humiliated, felt way too many ugly emotions rising in a long-conditioned response, a spark of anger at the forefront of them.



Stiffly, I replied, ``I\ldots let Brian know I was interested in him.  Romantically.  It was the truth.''



``Ahhhh,'' Alec responded.



``\emph{I knew it!}  Totally knew it from the second I saw you at his apartment!''  Aisha cackled.



I stole a glance at Brian and saw his expression hadn't changed in the least.  When he spoke, he did it with a small shake of his head, ``You could have been doing that to get me to let my guard down.''



``Bullshit,'' Alec retorted.



``What?'' Brian turned toward Alec.



``I said bullshit,'' Alec repeated himself.  ``Taylor said it herself, she sucks ass when it comes to lying and being smooth.''



``She lied well enough when she was keeping her undercover act a secret.''



``I didn't \emph{lie}, exactly,'' I said, quiet, ``I just didn't tell you.''



Nobody answered that statement.  I felt dumb for saying it, however true it may or may not have been.



Alec added to his earlier comment, ``I don't ever pay attention to that team drama shit, and \emph{I} picked up on the fact that she liked you.  It was so obvious it was irritating.''



It was strange, Alec was standing up for me.  He was insulting me while he did it, but he was still backing me up.



``That could have been an act,'' Brian stressed.  ``And even if it wasn't, it doesn't mean anything in the end.''



``You don't really believe that,'' Lisa replied, ``You're pissed at us.  I don't blame you.  I'd be pissed at us, too.  But you're only calling her a liar because it's a hell of a lot easier to be angry at her if you think the person you befriended was a fake.''



Brian sighed, loudly. ``Don't turn your power on me.''



``Who says I am?''



Chancing a look at Bitch, I saw she was pacing back and forth, each set of paces short and restless.  She didn't seem to have calmed down any.



I wasn't feeling much better myself.  I said as much, ``All I want is for things to go back to the way they were.''



``It's not that easy,'' Brian replied.  When I met his eyes, he looked away, his brow furrowing.



When had things been good?  What point in time was I so eager to return to, where I hadn't been wracked by guilt or nervousness?  By the time I got over my fear of getting caught, I'd run away from home and cut ties with my dad.  Then, before I could come to terms with \emph{that}, I'd found out about Dinah, which had affected me more than anything else.  I'd terrorized hostages, maimed a supervillain, hurt superheroes, but it was \emph{Dinah} that left me lying awake at night, feeling helpless, feeling like I was the scum of the earth.



And I couldn't help her from the outside.  That, more than anything, was why I was here.  I wasn't strong enough to fight Coil on my own, I couldn't go to the heroes and rely on them to handle it, not with Coil's power giving him \emph{two} attempts to escape, two attempts to any  counterattacks, two attempts to track down the person who'd informed on him and deal with her, and take his pick of the outcomes he wanted.  That wasn't even getting into the more complex uses of his abilities, only using one of his concurrent realities to try something, doing it over and over again until he got a result he wanted to keep.  I couldn't beat him in any kind of confrontation.



Lisa had convinced me.  I would only solve this by getting in Coil's good graces, talking to him as someone he could respect and listen to.



I couldn't do \emph{that} without convincing these guys to let me back on the team.



``No,'' I answered Brian, ``You're right.  It's not that easy.  But if you'll have me, I'm willing to work my ass off to make it up to you.  I'm pretty good as a member of this team, you know it.  If you want to monitor my every move, fine.  Any restrictions you want to put on me, fine.  I'll even give up my pay from Coil and any jobs we do.  Whatever you want.''



He shook his head, then asked me, ``\emph{Why}?  Why come back?''



``Because I've been to the shelters, I've walked the streets and seen what the Merchants and Chosen are doing out there.  I want to resolve this thing with Dinah.  Whether I like it or not, I know that the fastest way to get to that point where everything's okay again is working with Coil.''



Lisa spoke, ``I want her back on the team, obviously.  If we're voting, that's where my vote is going.''



``Mine too,'' Alec said, ``You're wound up, Brian, maybe it's Taylor being gone, maybe it's Aisha and your dad getting attacked, maybe it's the general situation with the city, but it's getting miserable to be around you.  Taylor was always the one who was on the same page as you, she'd be someone you can work with and talk to, at least.  \emph{You'll} be happier in the long run if she's around.  And \emph{we'll} be happier if you're not so fucking crabby.  `Sides, if she's giving up her pay, then it doesn't even cost us anything.''



``It costs us a lot,'' Brian said, his voice low, ``If mistrust and tension fucks up our team chemistry, especially if we start fucking up in the field, because of it.''



``So you're voting no?'' Lisa pressed him.



``Do I get a vote?'' Aisha cut in, before he could respond.



``No,'' Brian and Lisa refused her in unison.  Aisha made a face, but didn't seem too bothered.



``I don't want her on the team,'' Bitch spoke.



Brian shook his head, ``I don't know what to tell you, Rachel.  Alec's right, for once.  We need her.  We need the firepower, out there, at the very least.  Looking at this objectively, I think I'd have to say we should keep her.''



``Which is three votes for, one against,'' Regent noted.



Bitch threw the piece of chipboard she was carrying into the wall, hard.  One of the dogs started barking in response or in alarm.  She spat in my general direction and then stalked over to the far end of the room, her dogs trailing after her.  The metal stairs clanged with the impacts of her boots as she ascended to the next floor.



Lisa hesitated, then followed after.  Alec glanced at us, then put a hand on Aisha's shoulder and led her away, leaving Brian and me alone.



``Thank you,'' I said, quietly, to Brian.



Brian shook his head, ``Don't thank me.  Alec's right when he says that we'll probably get over this.  Maybe we'll even become friends again and get to the point where we can talk about it.  But that isn't going to happen today, and definitely not right here and now.''



``Okay,'' I replied.  But he was already walking away, leaving me standing alone at the entrance.



I had told myself I would rise above the likes of Sophia and Armsmaster.  I was all too aware of their flaws, and first and foremost among them was arrogance, pride.



So I'd swallowed mine.



\sectionbreak



\strong{Now}



There were so many ways this could go wrong.



Tattletale held a pair of binoculars and scanned the building in front of us.  ``There's movement.  We're good to go.''



``Go,'' Grue ordered.



Hitting the target wasn't so hard.  My bugs flowed in through windows and Bitch took the entrances.  Angelica had free rein, slow as she was, while the other dogs stayed on leash.  Grue hung back with Tattletale, Regent and me, while Imp moved forward, not charging in, but staying close.



The tricky part would be balancing this.  Too far one way or the other, and this got really ugly, really fast.



Our targets were looters, and they were well armed, though bullets were getting to be in shorter and shorter supply.  Coil had sources, and the Chosen did as well, but \emph{these} guys were from the Merchants.  They were vagrants, addicts and people who subsisted by mooching off the system.  When the system had failed, they'd latched on to the only group that would take them.  More had joined because it was safer and easier to be among the thugs, looters, scavengers and thieves than it was to be among the victims.  Safety in numbers.



They weren't strong or trained, and I couldn't call them brave.  That said, they were bolstered by a kind of desperation.  I'd seen it before, when I set my bugs on some of my enemies, how some panicked or saw the futility in fighting the swarm and others just fought on heedless of the damage they were taking and the pain they were feeling.



That same desperation posed an issue as far as our plan.  If we gave them a chance, they wouldn't hesitate to hurt or kill us.



They'd raided countless homes and businesses, taken everything of value they could uncover.  Phone lines were down everywhere, police response times far slower with the roads in the condition they were.  The looters had amassed a small fortune in stolen possessions, and intel said they were storing it here.  As reasonable a target as any.



My bugs drove the bulk of the looters out into the street.  Between Grue's darkness and Bitch's dogs, those same looters were driven back and cornered, hemmed in by the snarling beasts.



The second we had the situation under control, Shadow Stalker dropped out of the sky, a crossbow in each hand.  Tattletale and Grue were darted a second later.  She reloaded in a second using the cartridges that had been set on her gloves, then darted Imp and me.  By the time the dart embedded in the armor of my costume, Tattletale and Grue were slumping to the ground.



The fabric of my costume blocked the dart, so I didn't go down.  I drew my baton, snapped it out to its full length, and charged her.



She backed away, loading and firing another series of bolts at Regent and the dog closest to her.  By the time I reached her, she'd fired a second dart into the dog, then shot Bitch.



My baton passed through her, of course.  She walked through my arm, stepping right behind me, and then drove her knee into my side.  I grunted and fell over, and she retrieved and slammed a dart into my shoulder before I could recover.



\emph{Take it easy, Regent.}



Bitch managed to scream an order to her dogs before she `passed out', ``Go!''



The three newer dogs hesitated, but Angelica didn't.  She huffed out a snarl as she passed them, and the others took her lead and joined her in stampeding down the street until they disappeared from sight.



I laid in the water, aware of how cold it was, trying to ignore how \emph{dirty} it was.  My lenses afforded me an advantage in that I could watch what was going on without my open eyes giving anything away.  I saw Shadow Stalker touch her ear, then murmur something.  Tattletale had gone over everything Regent needed to know as far as that particular routine and the orders to give.



It took three minutes for the PRT to arrive.  I saw the green and white flashing lights and heard the splashing before anyone stepped into my field of view.



``Holy shit,'' one of the PRT uniforms spoke.



``Restrain them and throw them in the van,'' Shadow Stalker ordered him.



``Jao, get the containment foam,'' one uniform spoke.  The captain?



``They're tranquilized,'' Shadow Stalker spoke, sounding disinterested, ``Don't waste resources.''



``Protocol states we use containment foam, especially when there's an unknown.''



``The girl with the horns?  Mover three, teleports through shadows,'' Shadow Stalker lied.  ``None of them can escape restraints on their own.''



``But if Grue uses \emph{his} power-``



Shadow Stalker turned, then fired another dart into Grue.  ``Satisfied?''



We'd drained the darts of the sedative, of course.  Still, I was betting Grue would have words for Regent after this was over and done with.



The uniform didn't back down, ``No.  I want to know why you don't want them fully contained.''



``Because I've been up since five in the morning, it's well past midnight now, and I'm going to have to start doing fucking paperwork the second we get these guys in a cell.  I'm not allowed to walk away until they're in custody, so if I let you foam them, I'm going to have to wait another half an hour to an hour for the solvent to get mixed and brought to them, five or ten minutes for it to work.  Fuck that, they're down.  Listen to the hero who just took down a whole fucking team and get them in the truck.''



There was no reply to that, but a moment later, someone picked me up and started carrying me.  I maintained deep breaths, kept my body limp.  A few bugs congregated on me and the uniforms moving us, and I didn't do anything to dismiss them.  Maybe they would distract the uniform from the fact that any of us were still conscious.



 I was placed on the cool metal floor of the containment vehicle, my hands cuffed behind my back.  A few seconds later, someone was thrown over top of my upper body.  Too light to be Grue or Bitch.  It would be Imp or Regent.



The metal doors slammed shut and locked with an audible shift of internal machinery.



\emph{So many ways this could go wrong}.



We had safeguards, of course, including but not being limited to Coil's assistance.  Still, there was something profoundly unsettling about allowing myself to be cuffed and imprisoned.



``No ears on us,'' Tattletale murmured, ``We're good so long as we keep our voices down.''



``PRT is having words with the remaining `witnesses' who stuck around to grab loot after the dogs ran off,'' Regent informed us with a whisper.  ``They're backing up the story we wanted to sell.''



We'd passed one hurdle, at least.  The act could have gone either way – if we didn't sell it well enough, we could have wound up with the PRT arresting us for real.  If we timed it wrong or if one of the looters decided to attack us while we were pretending to be tranquilized, something ugly might have happened.



``You hit me way too hard,'' I murmured.



``Muscle memory,'' Regent replied.  ``Blame her, not me.''



``You alright, Imp?'' Grue asked.



``Duh,'' she replied.



It was a good few minutes before the truck bucked into motion.  Out of unspoken agreement, we stayed quiet, just to be absolutely sure that the driver wouldn't hear us.  It was maybe ten or fifteen minutes before we arrived.



``We're at their headquarters,'' Regent spoke, his voice hushed.



``Then we're in good shape,'' Grue answered.



``Weld and the Wards are coming out to meet Shadow Stalker.  Heads up.''



The back door of the van opened.  I could feel cooler air enter the enclosed space.  There was an audible click of a gun, as if they were anticipating an attack the moment the doors opened.



``Wow,'' one of the boys commented.  I was guessing it was Kid Win or Clockblocker.  ``How'd you pull that off?''



``They were distracted, I picked them off.  \emph{That} little freak that saw me with my mask off was wearing armor, so I had to resort to CQC,'' Shadow Stalker made it sound matter-of-fact.



``Riiiight,'' one of the other boys said, sarcastic.



``You're quiet, Weld,'' a girl's voice.  Vista?



Who was Weld?



``Basking in how fucking awesome I am?'' Shadow Stalker gloated.



``Maybe later.  For now\ldots'' the accented male voice spoke, ``Just satisfy my curiosity.  You know the passwords we memorize each week, and you know why we memorize them, right?''



``Yeah,'' Shadow Stalker replied.



One of the other boys spoke, ``For any interaction with any flagged shifter or,'' the boy paused, ``master.  \emph{Oh}.''



``So,'' Weld said, ``Keeping in mind that Regent is the highest rated Master in the city, I'd like for you to give us this week's password.''



There was a pause.



``Comanche Six-six-two,'' Shadow Stalker spoke.



Another pause.



``Alright,'' Weld confirmed, ``Pick 'em up and haul them into the holding cells.''



It was all I could do to stay still and not show my relief.  Tattletale had anticipated this much, had drilled Regent on it, but she \emph{had} been wrong in the past.



Imp was lifted from on top of me, and Tattletale was picked up next, from right beside me.



I was among the last to get lifted off the floor of the truck.  Shadow Stalker held me until a pair of PRT uniforms could haul me to my feet and lift me by my armpits, my feet dragging on the ground, my head hanging.  I chanced a partial opening of my eyes, knowing my lenses would hide them, to sneak a sidelong peek at this `Weld'.  Metal skin, metal hair, and a strange melted-junkyard texture to his shoulders.  I'd crossed paths with him before the Endbringer event.



He spoke, his voice quiet enough that it was probably intended for just him and Sophia, ``Where are the dogs?''



``Tranquilized them, they didn't go down.  Ran when Hellhound dropped.''



Weld nodded, ``This is good work, but it doesn't excuse or make up for what happened earlier.''



``Whatever,'' Shadow Stalker replied.



``No.  This is serious.  You assaulted a team member.  I'm not about to let that slide.''



On one level, I wasn't surprised to hear that.  I knew, cognitively, that she had that kind of personality.   But emotionally?  I hadn't really believed it.  It caught me off guard to hear she was that big a problem in the Wards, as well.



A few seconds passed before she finally asked, ``What are you going to do?''



``After these guys are securely in custody, we're going to have words with the Director.  She wants you on this team, for whatever reason, so I don't expect your probation will be broken, but there's going to be consequences.''



``Fuck,'' Shadow Stalker said.



``\emph{And} you're going to apologize to Kid Win.  I don't ever want you assaulting him again.''



Shadow Stalker paused.  ``Stop fucking testing me.  I'm too tired for this.  It wasn't Kid Win.''



Weld nodded.  I blinked a few times in surprise.  Tattletale hadn't gone into this, hadn't anticipated it. Weld had just tried to trip up Regent/Shadow Stalker, and Regent had anticipated it.  A bullet dodged.



I saw we were passing by a front desk.  I'd never been in the building, but I had passed by it a few times.  It was surprisingly empty.  There weren't many PRT uniforms around, either.



``Who was it, then?'' Weld asked.  It took me a second to parse what he meant.



Shadow Stalker groaned, ``Fuck off!  It's me.''



``Hey,'' he turned, putting one hand on her shoulder to stop her mid-stride.  ``Who was it?''



She glanced at the group.  Clockblocker, Kid Win, Vista, and the girl from the Endbringer fight who called herself Flechette.



``Clockblocker,'' she guessed.



Weld didn't move an inch, and my gut told me Regent/Shadow Stalker was off the mark.  My heart sank.



Clockblocker and Kid Win stopped walking and looked our way curiously.



``Heads up!  Trap!'' Weld shouted.





