





We burst into action the moment Weld called out his warning.



Bitch drove her shoulder into the PRT uniform that held her back, then backed towards the front desk.  Weld had already changed his hand into what looked like a baseball bat with four sides to it, long enough to reach from his wrist to the ground.  Studs the size of golf balls ran down each of the four faces, with a blunted spike on the end.



Weld and Flechette were variables we hadn't planned for.  It was unfortunate, but Weld in particular was also \emph{very} well equipped for the task of keeping us from retreating back to the front door.



Weld swung at Shadow Stalker, but his club passed through her.  Fearless, she stepped close and punched the metal arrowhead of one of her crossbows into his right eye.  He stepped back a few steps, one hand going to his eye, and she threw herself at him, bringing her knees to her chest and then kicking out.  Her feet slammed into his chest, and pushed him further back.  Weld only staggered back a short distance, and it was Shadow Stalker who landed hard on her back.  Kicking a five-foot-nine-inch block of metal had to hurt, but Regent doesn't exactly have to be careful with Shadow Stalker's body.



Bitch slipped past the pair of them, reaching the front door.  I could hear her whistle at a volume that I doubted I could \emph{scream}.



Grue and Regent were already free of their cuffs, the three PRT uniforms closest to them lying down on the ground.  Tattletale was grinning at the four wards at the end of the hall closest to the elevator – Kid Win, Clockblocker, Flechette and Vista.  The laughter didn't belong to Tattletale, however.  It was cackling, sounding like someone having way too much fun.



Flechette shouted, ``They've got someone with the Stranger classification!''



We did?



The Wards recovered fast enough.  Vista was working to distort the ends of the hallway, the front doors, and the elevator at the end of the hall into impassable terrain.  Flechette fired a shot at Grue, pinning him to the ground, quickly loaded and fired a second, rooting his feet to the ground.



Flechette was loading for a third shot when a girl in black clothing with a horned demon mask and black scarf struck her weapon with a fire axe, splitting the metallic string and knocking it from her hand.



The girl with the horns was on our side, wait- I could almost remember her.  Some relation to Grue.



Then it slipped from my recollection, and I was distracted by the fact that Flechette was disarmed, her weapon broken.  How had that happened?



I couldn't afford to worry about it.  I had to focus on contributing.



I released the bugs from beneath my costume, drawing them out from beneath the panels of my armor and the compartment at my back where I kept my equipment and weapons.



I'd known I wouldn't be able to bring many bugs, and that it would be difficult to get more on site with a clean, sturdily built structure like this one.  I could gather a swarm, but it would be a few minutes before the bugs arrived en-masse.  I might have started sooner if I hadn't been so concerned about alerting someone and giving us away.



The nine hundred and seventy bugs that poured forth were roughly equal numbers of bees, wasps, spiders, mosquitoes and cockroaches.  It was a smaller number than it sounded like, and their deployment was slower because of the way I had them arranged, stingers and abdomens carefully kept out of contact with one another.



I hadn't come without a plan.



The bugs found their way to Vista, Flechette, and Kid Win, the only young heroes with exposed skin, at roughly the same time as they managed to get beneath the masks and protective clothing of the two PRT uniforms that were holding me.



At first the teenaged heroes swatted at themselves and backed away, as was usual.  The `fun house mirror' distortion at the exits stopped spreading as Vista's concentration broke, and Flechette dropped one of the small lengths of pointed metal that she'd been withdrawing from her belt.



Then Kid Win cried out, his words raw and barely intelligible because he was also screaming as he shouted them, ``It burns!''



Capsaicin was the chemical that made hot peppers burn your tongue.  It was also the active ingredient in pepper spray.  I'd used pepper spray a few times, myself, and I'd had it accidentally used on me when I'd been out in costume, rather recently.  At the time, I'd stepped in to help fight back a crew of the Merchants up near the old Boardwalk.  They'd been aiming to loot the stores, and a contingent of people who'd created an armed force in the ruins of the upscale shopping district had stepped up to fight them off.  One of the defenders had sprayed a looter, and caught me in the effect as well, maybe intentionally.



I'd stepped back and let my bugs do the work while I recovered.  After the fight had wrapped up and I'd headed back to a shelter in my civilian guise, I'd been left to consider the fact that my bugs were vulnerable to the pepper spray.  By all rights, I should have been alerted to that fact the night I sprayed Velocity at the fundraiser, but I hadn't been able to keep that many bugs on him, then, and I'd had many, many other distractions at the time.  It had escaped my attention.



While sitting up all night at the shelter, with kids crying and wailing and assholes making noise to intentionally piss off the other hundred people in the room, I'd had time to think.  The next morning, I'd woken up, donned my costume and started experimenting to see if I could protect my bugs somehow.  Pepper spray was only one thing.  I was bound, sooner or later, to go up against someone who used some kind of bug spray or gas on my tiny minions.



Had I found a solution?  Not so much.



I \emph{had} discovered that I could use hair spray to coat the abdomens and stingers of my bugs, and \emph{then} dip said abdomens and stings into some of the capsaicin. With a bowl of each in liquid form and two single file lines of bugs, I could dose a fair number before I went out in costume.  It did wind up killing some of the less durable ones eventually, either through the hairspray obstructing breathing or the capsaicin getting on the bug, but the end result was that I'd stumbled onto a weapon while trying to experiment with defenses.  I \emph{had} figured out how to use my bugs as a delivery mechanism, smearing pepper spray onto fresh stings and bites.  I could jam their abdomens into people's noses, mouths and eyes to cause intense burning and pain to the point that it made them nauseous.



Flechette screamed, falling to her knees, her hands to her face.  One of the PRT uniforms that was holding me let me go to stagger blindly toward the front desk.  I struggled to get away from the other one, but he held me tight even as he bent over, threatening to topple to the ground with me beneath him.



So yeah.  It worked.



Clockblocker had been in the lead of the group as we'd all headed toward the elevator, and had been delayed by the fallen PRT uniforms and his collapsing teammates.  His costume covered his entire body, preventing the bugs from getting to him, so once he got past his allies, there wasn't much to get in his way.  He charged straight for Grue, and Grue responded by shrouding his immediate vicinity in darkness, though he couldn't do much else.  One of Flechette's bolts had nailed the sides of one of his boots to the ground – the other shot had missed, maybe because she couldn't see his foot and hadn't wanted to put a spike through his actual flesh.



Clockblocker closed the distance and plunged into the darkness after Grue.  He emerged out the other side, and the darkness dissipated behind him, revealing Grue, frozen in time.  Even the shadows smouldering around Grue's body faded, revealing his motorcycle leathers and the helmet with the skull-face molded into it.



Which was bad.  It could be up to ten minutes until Grue was back in action, and we couldn't necessarily afford to babysit his body until he reanimated.



The other PRT officer that was holding me broke away when a girl with a horned mask drove the wooden end of a fire axe into his shoulder.  Regent made Clockblocker stumble, and the horned girl shoved the PRT officer into the boy.  They both fell in a heap.



``Hey!'' A girl shouted.  I looked and saw a horned girl crouched by one of the fallen PRT officers, holding the foam sprayer.  Imp.  Right, it was Imp.  She looked at Tattletale, ``It won't fire!''



Tattletale hurried over, grabbed the fallen officer's arm, and lifted it over to the handle of the gun.  She put his finger on the trigger and aimed the gun at Clockblocker, unloading spray on top of his upper body just as he managed to heave the fallen officer off of himself.



Flechette threw a dart into the foam canister, and both Imp and Tattletale backed away as foam began spilling out of the hole, rapidly expanding to partially cover the uniformed officer.  After a moment's pause, she threw a spike of metal into every other canister on the other fallen guards.  One even erupted into a pressurized spray, jetting up at an angle to hit the wall, creating a growing barrier a few feet in front of me, partially blocking me from reaching the rest of the combatants.



Before Flechette could turn her darts on us, Regent reached out, causing her to fumble and drop it.  A second later, he grunted and fell to all fours.  Nothing I could see had touched him.



\emph{A backfire?  So easily?}



I was already turning to check when a primal scream tore its way from Shadow Stalker's throat.



She'd been fighting with Weld, and Weld almost fell over when he swung and she \emph{didn't} enter her shadow state.  He couldn't stop all of his momentum, but he stepped close and let his upper arm hit her instead.  They stumbled together, Shadow Stalker continuing to scream like she was trying to empty her lungs of every last trace of oxygen.



She raised her crossbow in my general direction, then moved, almost staggered, one step to the side.  From her new vantage point, she targeted Regent; her movements weren't fluid, and her shot flew past him.  It hit Tattletale instead with a glancing blow, raking across her collarbone to penetrate her shoulder at a shallow angle.  Tattletale was spun off-balance and fell.



Shadow Stalker moved to load her crossbows, but her movements were jittery and jerky to an even greater extent than they had been a second ago.  She stopped midway through the motion, her head turning as she looked from one hand to the other, and then looked up at Weld, who was in close proximity to her.



``H-h-help.''  She stuttered.



A fraction of a second later, Regent was in control again, and Shadow Stalker was attempting to repeat her maneuver from earlier, driving an arrowhead into Weld's other eye, moving quickly and with as much grace as ever.  He swatted her hand aside, and she entered her shadow state to avoid his follow-up swing with his club.



A series of crashes and the sound of breaking glass showering onto tile announced the arrival of Bitch's dogs.  They had barreled their way through the bulletproof glass that led into the lobby.  Weld spun to face them, and Shadow Stalker abandoned her fight with him, using the opportunity to finish reloading her crossbows and fire one at Vista, who was hunkered down on the floor, my swarm all over her.  At least the girl wouldn't be in further pain from what my bugs had done.  I could inflict pain if it meant getting a job done properly.  That didn't mean I liked doing it.



``Shadow Stalker is conscious in there!?'' Weld shouted, his back to us, attention on the three advancing dogs.  None of the dogs were as big as they could get, Bitch couldn't manage them if they were too large, but it was still the equivalent of three rather agile bears or three unnecessarily burly jungle cats joining the fight, each with some added natural protection in the horned growths of bone and calcified muscle.



``Since a little while ago,'' Regent answered.



That was disturbing.  I didn't have a better way of putting it.  I'd almost been paralyzed by Leviathan in the Endbringer attack, but even before that, the idea of being left conscious but unable to move of my own volition had always spooked me.



I'd never had a relative in the hospital suffering from anything like that, and I couldn't remember seeing any movies or shows on television that might have put the idea in my head at an impressionable age.  Still, it was one of the first places my mind went when I thought about worst case scenarios and horrific fates.  It had been in my thoughts more over the past two or three years, and the idea had been showcased in more than one nightmare over the past two weeks.



Maybe it was more general than that.  Not a fear of paralysis, specifically, but of helplessness.



The dogs started fighting with Weld, and it didn't seem to be a fight they would win.  They were faster, they had the advantages of numbers, I even suspected they were stronger.  Despite that, when it came down to it, Weld was a walking, talking statue.  They could hit him hard enough to knock him down, but they couldn't set their teeth into his flesh or deal any lasting damage.  When Weld hit \emph{them}, by contrast, the hits were most definitely felt.



Still, their intervention did allow us to turn our focus to the others.  Vista was out of action, as was Clockblocker.



``Help Skitter!'' Tattletale ordered, sounding urgent as she turned her attention to the remaining Wards that stood between us and the elevator.  Who was she talking to?



Then I felt hands at my back.  I flinched, but they held firm.  A second later I felt my cuffs come undone.  Imp.  Right.



I was getting the distinct impression that it was easier to recall her and react as if she were present if I hadn't been actively trying to pay attention to her.  It was almost as if actively trying to commit her presence to memory had the opposite effect.  Except how was I supposed to put that knowledge into practice, if acting on that knowledge counted as recognizing her presence?



I didn't get a chance to work it out, because Imp was gone from behind me a moment later, and we were faced with the issue of dealing with Flechette and Kid Win and the fact that our movements were getting more and more limited by the growing piles of adhesive, nigh-indestructible foam.



Kid Win had pulled himself together enough to draw a small blue pistol from his waist.  I tensed, bending my knees and shifting my weight to the balls of my feet so I could move the instant he aimed at me.



He didn't fire it, though.  Instead, he slapped his chest, and the armor there opened up, revealing a circular depression.  He slammed the little blue gun there, where the weapon stuck like it was glued in, or maybe because of a magnet.  The chest portion of his armor closed up.



He staggered to his feet, swatted at his face, then looked like he immediately regretted doing that, judging by his pained grunt and gritted teeth.  His costume started to light up, glowing with a silvery light where it had been gold, before.  Two pear-shaped pieces of metal that had been attached to the armor on his shoulders raised into the air, floating.



Abruptly the pieces of metal jerked so the smaller ends pointed at us, and they each belched out blue sparks the size of softballs.



Imp appeared as she ducked out of the way of one, while Regent avoided the other.  Tattletale was still on the ground, one hand to her shoulder, and the shots passed well over her.



I didn't see the need to dodge – the shots weren't fast moving, and both seemed ready to collide with the walls on either side of me.  What I didn't expect was for their trajectory to slow, then stop altogether, before they hit the wall.  Picking up speed, they headed back toward Kid Win.



``Heads up!'' I shouted.  Imp and Regent turned just in time to avoid the boomeranging projectiles, but the distraction nearly cost them as the guns above Kid Win's shoulders blasted off another two `sparks'.



``What the hell!?'' Imp shouted.  The returning sparks had fallen into a lazy orbit around Kid Win.  Two, then four, then six sparks orbited him, with more joining the mass.  As the seventh and eighth sparks joined the ring that spiraled around Kid Win, arcs and flashes of electricity began to dance between them, making it into a loose ring that encircled him.  He advanced a few steps.



My bugs were dying in droves with the residual electricity, but Kid Win, at least, was largely incapacitated, his eyes swollen nearly shut, with some bugs gathered over and around his eyes to further obscure his vision.



I'd read up on the Wards, when I first got my powers, I knew they weren't allowed to use lethal weapons.  Shadow Stalker had to use tranquilizer darts instead of real arrows, though she violated that rule often enough, and this device of Kid Win's, no matter how intimidating, wouldn't be allowed to do any sort of serious injury.



``Shadow Stalker!'' I shouted, ``Charge Kid Win!''  Expendable assets.



``Can't!'' she and Regent shouted in unison, ``It'll disrupt my control!''



Hearing that, Kid Win turned and fired a pair of sparks in their general direction.  The sparks flew further and faster, and they reached far enough that I actually had to dodge those.  One slammed into the spray of foam that the canister was blasting into the wall, while the other sailed toward Shadow Stalker, but stopped a few feet short and then looped back toward Kid Win.



That left one option.



Bitch wasn't around, which left it to me.  I whistled, hard, getting the attention of the dogs.  When the dog with the squarish, almost snoutless head turned my way.  He'd be the bulldog puppy, Bentley.  I took a step toward Kid Win, pointed at the young hero, then shouted, ``Get him!''



A ragged, horn encrusted tongue lolling out one side of his mouth, Bentley eagerly tromped past Weld, who lashed out with his club but only grazed Bentley's rear flank.  Recklessly, the dog charged Kid Win, slamming into him, taking the full brunt of the ring of vibrantly blue electricity.



The dog and the boy crashed to the ground together, and skidded far enough toward the elevator that they collided with Flechette, who had retreated from the storm of blue sparks, her back to the elevator.    Bentley stood, flashes of brilliant blue light crackling at the chain that was rigged around his muzzle.  He limped strangely, but it wasn't due to any injury.  From what I could tell, he'd stepped in some of the foam as he ran, and his foot was sticking to the floor.  More foam had splashed his shoulder.  In any event, the two teenage heroes were down, and it looked like the sparks had done more to incapacitate them than it had the puppy.



``Good boy!'' I called out, ``Good Bentley!''  His tail, shorter than any of the other dogs, wagged at the attention.



Shadow Stalker, Imp and the two remaining dogs had Weld on his heels, Imp doing her best to smack him in the face with the fire axe and have the metal obscure his vision.  Bitch slipped past the melee.  I looked away, tried to figure out a simple way to get by the spout of foam that was still sputtering out of the hole Flechette's dart had made in the tank while still avoiding the flailing PRT uniform that was kneeling a short distance from me.



The next thing I knew, I was being slammed into a wall, hard.  For one moment I thought it was Weld, but I heard the snarling of the dogs and the noise of impacts.  I knew Weld would have hit me harder.



No, it was Bitch.



``You do \emph{not} give orders to my dogs!'' she growled in my ear.  ``You do \emph{not} get a say in whether they are good or bad!  Do that again and I will order them to chew you up and spit you out!''



``Bitch!'' Tattletale shouted, I could almost see her out of the corner of my eye, cringing at the pain shouting caused her.  She still had the crossbow bolt sticking out of her shoulder, ``Not the time!''



Bitch made a feral noise as she broke away from me, releasing me from my position against the wall.  I turned around to see her grabbing the flailing soldier and throwing him on top of the foam canister that was still spraying in fizzing spurts.  She walked on him to head toward the elevator.  Reluctantly, I followed.



Tattletale got Imp's help in dragging Vista to the elevator door.  Regent took over and helped Imp hold Vista there, their fingers prying her eyes open until the retinal scan finished, then dragged her inside.



``Come on!'' Tattletale urged us.



I looked back at Grue.



``Bitch, the dogs and Shadow Stalker will be here to protect him!'' she called out.



I considered a moment, then nodded.  I joined the rest of the group in the elevator, and we headed down to the lowest floors.



``Cameras,'' Tattletale spoke.  I nodded, and sent bugs into the room, found the surveillance cameras that were spaced at regular intervals around the room, and covered the lenses with bugs.



We exited the elevator, stepping into the Ward's headquarters.  The room was vast, with a high domed ceiling that probably made this floor three stories deep.  A computer console with a dozen monitors sat to our right, and the far end seemed to be walled off into several smaller rooms.  The signs at the doors to the left implied they led off to the bathrooms.



To think that, if things had gone a little differently, I might have wound up here.



Tattletale was at the computer in an instant, reaching into her belt pockets to retrieve a series of USB thumb drives, which she slid into the available ports of the computer.  The monitors went to a blue screen.  As she typed, the word `JPIGGOT' appeared on each monitor.  When that word disappeared from the screen, she typed a password, a row of asterisks appearing on the screens, twelve or thirteen characters long.



Then gibberish filled the screen.  Some looked like code, much looked like random numbers, letters and symbols, even hearts, spades and smiley faces.  Some of the snippets of code appeared to be file names.



``This should be every document the PRT has on file for their teams, barring the most secure documents, which wouldn't be kept accessible, even in this isolated network.''  She handed me a pad of gauze from her belt.



``How long?'' I asked.  I snapped the feathered end off the crossbow bolt, then pushed it out the other side.  The arrowhead wouldn't take to being pulled out backward.



``Two minutes.''



``But we may have to wait up to ten, depending on when Clockblocker's power wears off.''  While I talked, I held the gauze to her shoulder with one hand and took the offered tape with the other.  There was a rip in her costume, and I opted to tear it a little wider and put the gauze beneath before taping it on, to let the skintight fabric hold it firm.



``Bad luck he got one of us, yeah.''  Tattletale made a face, ``Regent, let us know if there's movement from Grue up there, through Shadow Stalker.''



``We're going to have to fight our way through their reinforcements if we wait too long,'' Regent said.



``Probably.  But not the Protectorate.  The only one who could get here fast enough to matter would be Velocity, and he's dead.''



``They could have new members like the Wards did,'' I said.



Tattletale frowned, ``True.  They recruited those guys fast.  Especially since they've been here a few days.''



``Either way, we should make a quick exit,'' I advised.  ``Fast as we can manage, anyways, with Grue being stuck like he is.''



As the screen filled with more gibberish, reaching the point where there was more white text than blue background, we prepared to make our exit.



``Elevator's down.''



``Of course it is,'' Tattletale sighed, ``There are stairs, through the door by the little window, where the tourists look in,'' Tattletale said.  She waited with one hand poised over the USB drive.



A half second before the last blue dot on the screen disappeared, the entire room plunged into darkness.  The computer screens went black.



Silence reigned for a few heartbeats.  It wasn't Grue's power, though.  I could hear my own breathing.



``Someone cut the power?'' Imp asked.



``No,'' I heard Tattletale, ``Separate power source, buried deeper beneath the building.  Same with the computers, there's nothing upstairs or even in the city that could turn them off.  They're hooked up to that power source, they've got internal batteries, and the only external connection is by satellite linkup.  They might terminate our connection to the computer database via the satellite feed, but not the lights.''



``So this is bad?'' Imp asked.



A computer generated face appeared on the computer screens, illuminating us and our immediate surroundings with the pale glow the image cast.  I didn't recognize the face, but I could guess.



\emph{Dragon.  She was onto us.}  Yeah, that was pretty bad, as these things went.





