





I could detect a definite note of irritation in Dragon's voice, despite how she'd synthesized it to mask her tone, inflection and speech patterns.  ``You were tampering with my system,'' she accused us.



In the dim light the monitors shed, I could see Imp trying the door by the stairs.  It didn't open.  I gave it a try and verified it had sealed shut.  I wasn't entirely sure why I'd expected a different result.  Maybe I'd been hoping Imp had been making a horribly timed joke?  It wouldn't be beyond her.



``We \emph{were}, but we're done now, so we'll be on our way,'' Tattletale called out, her voice raised to be picked up by whatever microphones Dragon was using to listen in on us.  I could see her pulling the USB drives from the computer.



Dragon informed us,  ``I'm reading the files and notes we have on you as we speak.  Tattletale, it seems you have a penchant for needling your opponents.  Rest assured, if you intend to try it, I won't rise to the bait.''



Imp hefted her fire axe and struck just beside the handle of the door.  The door itself was hollow, but it was made of something like fiberglass, and the axe only made a small hole, a half inch across and less than two inches long.  She struck again, slightly higher.



``So few think they will,'' Tattletale said with a grin.  ``So.  I guess you've locked us in here, huh?''



``Yes.  You'll get out, perhaps, but not before reinforcements arrive.''



``We'll see,'' Tattletale answered.  She began moving toward the Wards' quarters.  She looked from one security camera to the next, as if trying to figure out if she was being watched.  I did have my bugs covering the lenses of the cameras I'd been able to find, but that wasn't to say that they could have something more concealed.



It was kind of creepy, that the kids here were observed constantly like that.



``You tried to steal official data, \emph{and} you put a virus on my system.  Epeios' work, I believe.  I'm more insulted by the fact that you went to that hack than I am about the virus.''



``Had to slow you guys down somehow,'' Tattletale called out.  She motioned to me, and I hurried toward her.  Imp let go of the axe to rub and shake her hand.  Regent grabbed the weapon to take over the job of hacking at the door.



I followed Tattletale into one of the rooms at the other end of the Ward's headquarters.  Pieces of technology littered the area.  There was a small bed in one corner so littered with pieces of junk, screws, scraps of metal and unfinished projects that I doubted the occupant had used it to sleep in a long time.



Kid Win's room, had to be.



``Gear up,'' Tattletale said.



``What?''



``Taking a tinker's stuff to keep is a bad idea, what with GPS signals and tracking and all that, but at the very least, we can use this to get out.''  She swept her arm over the room, where stuff lay on every surface.



Dragon's voice echoed through the chamber, ``I can hear you, Tattletale.  Do \emph{not} use a tinker's devices.  Power supplies can overload, weapons and equipment can misfire.  Only the tinker who made it can verify the devices as safe and operate them properly.''



``Right, sure,'' Tattletale called out with a note of sarcasm in her voice.  ``Because it's not like there's any high profile mercenaries out there who've made a career off of using a tinker's stuff.''



Dragon didn't reply.  Had Tattletale found a sore spot?  I knew the Dragonslayers were mercenaries who had taken the parts of one of Dragon's armored suits to outfit themselves as high tech mercenaries.



Tattletale looked up and glanced around the room, then whispered to me, ``Don't worry about misfires.  I think my power will help us spot those.''



I wanted to believe her, but she'd been wrong before.  It would be Murphy's law for her power to go awry here, with us blowing our faces off or something.



Still, I didn't stop her from picking up a gun without a handle.  She pointed it at the wall and pulled the trigger that sort of dangled beneath the gun.  A yellow dot appeared on the wall, then started smoking.  She glanced over her shoulder, and when I turned to see what she was looking at, I saw a matching dot on the wall.  She moved the gun, and the dots both moved.



``Laser with invisible beam.  Ricochets,'' she murmured.  ``Doesn't burn that hot, wouldn't do any damage to anything or anyone.  Wouldn't incapacitate our opposition or get us out of here.''  She put it aside.  ``Look for something better.''



Dangers aside, borrowing Kid Win's stuff wasn't a bad idea.  At the speed Regent and Imp were cutting through the door handle, I figured it would be minutes before they were through.  We had to get out of here before the Protectorate arrived.  Even with their numbers cut by recent casualties and injuries, that would be very, very bad for us.



I uncovered three guns that looked like they might work.  Tattletale looked them over.  ``Nonlethal flamethrower that probably didn't pass review, some kind of forcefield barrier cannon and some kind of gun for fighting bigger foes.  Nothing too dangerous, but don't point them at any of the rest of us until you've tested 'em out.''



Nodding, I lifted the one that was five feet long, needle-thin and spearlike.  I worked to get it out of Kid Win's quarters and aimed it at the largest chair, by the computers.  I depressed the trigger, and a blue flame the length of my forearm spat out the end, consuming the chair.  The seat bent under the heat, melted plastic pooling on the floor, an acrid smell assaulting my nostrils.  The flames that licked the remaining material cast some extra light on our surroundings.  It was pretty thorough destruction for less than two seconds of sustained fire.



\emph{How the hell is that nonlethal?}



I hurried over to the door, and both Imp and Regent backed away to let me fire.  I pulled the trigger\ldots nothing.



``He took the power and fuel supply from that to use for something else, put crap components in there instead!  Let it recharge!'' Tattletale shouted across the room, ``Almost one minute before you can shoot again!''



\emph{Fuck}.



Dragon would have overheard that, but she didn't comment.  Instead, a sprinkler system kicked into gear, misting down from the ceiling.  Though the quantity of water was low, the effect on the burning chair was immediate, and the flames disappeared with surprising quickness.  What little of the moisture soaked into my mask tasted faintly bitter.



Then Dragon shut off the monitors, plunging us into absolute darkness.



I left the weapon with Imp and hurried over to the other guns, using the few bugs I had with me to `feel' my way, sensing their locations and identifying anything I might trip over.  The second gun, though it had looked more complete than any of the others, had two triggers on the front and two by the handle.  I tried various combinations and got nowhere.



The last gun was heavy.  I hefted it with both hands, then told Regent and Imp to move aside as I aimed it at the door.  Didn't want to waste any first shots if this was going to take forever to recharge as well.  The gun vibrated, rattled, and shuddered for a full five seconds before it fired.  The shot didn't cast any light, but it struck the door with enough force that the entire door buckled outward.  I hit the door with my shoulder, and the upper hinge came free.  There was a light in the stairwell, shedding some meager light on us.



``Tattletale!'' I called out.  ``We got through!''



By the time Tattletale reached us, Regent and I had brought the door down.  The lock was still extending from the handle to the frame, but we'd taken the door off its hinges, and we were free to pull the door open from the other side.  We hurried into the stairwell and began heading back upstairs.



``Fight upstairs is going south, we need to step in, fast,'' Regent spoke.  I felt out with my bugs to get a sense of where each of the combatants were, then nodded a hasty agreement.  I began taking the stairs two at a time, though the gun I carried had to weigh a good thirty or forty pounds.



We were halfway up when we came across a pair of unconscious PRT officers.  I looked at Tattletale.



``Imp did this,'' she told Regent and me.  ``She went ahead, remember?''



It took me a few seconds to realize who she meant.  Damn it, having to keep track of Imp and having her power throwing me off my stride was getting to be annoying.  The team prior to now had a kind of synergy, with the way my bugs and Tattletale's power let us deal with Grue's darkness, and how the dogs could smell opponents through it.



We found Imp at the top of the stairs, aiming the spearlike gun.  The blue flame poured out, melting a large hole in the fiberglass.  We crouched in the stairwell as Imp opened the door.  I was so distracted by the sight of the PRT uniforms waiting for us in the hallway that I didn't see where Imp went.



The reaction wasn't as strong or immediate as I would have expected, given the burst of flame and the door opening.  A side effect of Imp being the one to carry it out?  One person shouted and alerted the others.  Regent used his power on the one closest to him, causing him to stumble sideways into his comrades. Their ranks descended into chaos.



I readied the few bugs I had on my person, then hefted my borrowed gun.  I backed down a stair as I asked Tattletale, ``This thing is nonlethal, right?''



She didn't have an answer for me.  Instead, she yelped out, ``Back!''



She practically pushed me down the stairs, and I caught a glimpse of her covering her ears, shutting her eyes.  Despite the fact that I was on the verge of landing face first on the landing of the stairwell, I didn't use my hands to stop myself.  I turned to take the impact with my shoulder, tucked my chin to my chest and covered my ears.  Regent jumped out of my way as I landed, his arms pressed against the sides of his head.



It had to have been a grenade.  The blast ripped through the upstairs hallway, and left me gasping even from inside the stairwell.  Tattletale was up before I was, hauling me to my feet and up the stairs, Regent followed just behind us.



The grenade had been of the nonlethal variety, but not quite a flashbang.  The gathered soldiers were reeling, stunned, and Imp was crouched by the only one who was still conscious.  She drew a taser from her sleeve, tagged him, then stood.  She had one of the PRT's grenade launchers slung over one shoulder, the flamethrower-thing in one hand, and the taser in the other.  She handed off the grenade launcher to Regent, then put the taser away, holding the flamethrower.



To reach the hallway where Grue and the elevator were, we had to head out past the gift shop and around the front desk.  Everyone we'd left behind was still there, friend and foe, but things hadn't gone well in our absence.



We found Bitch and Shadow Stalker backed against the elevator at the far end of the hallway.  The three dogs were spread out between them and Weld, limp and unmoving.  They'd shrunk down almost to their normal size.  I had to watch for a few seconds before I could see the rise and fall of Sirius' chest and verify he was alive.



Weld stood beside Grue, binding a length of cord around our leader.  The way he was positioned, Bitch wasn't able to get by, and I could only assume that Regent had Shadow Stalker there because Bitch lacked the means to defend herself solo.  The elevator, naturally, wasn't running.



I lifted the heavy gun, then aimed it at Weld and Grue.



``Where did you get those guns?'' Weld asked, squaring his shoulders as he turned to face us.



``Borrowed 'em,'' Tattletale smirked.  Then she fired the gun she was carrying.  An arc of electricity crackled between the nozzle of her gun and Weld.  Seemingly unconcerned, he started running towards us, metal feet pounding on the tile.



Tattletale backed up one step, and I took that as my cue to back up three. This guy could hit hard, and none of us was capable of going toe-to-toe with him.



There was no need to worry, as the lightning gun's effects added up and Weld collapsed to the ground before he got halfway to us.  Tattletale stopped firing, and I could see that the metal of Weld's body was glowing with the heat he'd absorbed.  She stepped closer and swung her gun at him, smacking him across the face with the barrel.  It stuck, and she swiftly backed up.  I wouldn't have thought he was that hot, that the metal would bond.



Weld staggered to his feet and tore the gun away with both hands, leaving a melted mess that extended from his cheekbone to his forehead on one side of his face.  Gun removed, he started reforming his hands into sticks, four feet long, with the ends curved into blunted hooks.



I raised the gun that had nearly knocked the door off its hinges and pulled the trigger, aiming it at both Weld and Grue.  Nothing.  Whether it was due to a lack of charge, a malfunction, or whatever, it just didn't work.



Weld began to charge us, and he was nearly to us when Imp stepped in his way and tried to fire.



``Don't--'' Tattletale started.



As with my gun, the flamethrower didn't work.  Weld clobbered her just as she was beginning to utter a swear word, catching her with both hands to fling her aside.  She tumbled into a sign.  That put him only a few paces from me.



Shadow Stalker was already running toward us.  She entered her shadow state to leap forward, interjecting herself between us and him before going solid.  There was no grace in her movement as she threw herself at him, no particular technique she employed.  They slammed into one another, and she went limp, her body getting tangled up in his legs as he trampled her to the ground.



A short distance from us, Regent fell to one knee, grunting slightly.  A backfire?  Or something else?



More out of an attempt to minimize the damage to Shadow Stalker than actually being bowled over, Weld fell.  I did as Tattletale had done before, and struck Weld with the metal of my gun's barrel.  As I'd hoped, he was still hot enough that the gun bonded to the metal of his body, I could help to hamper his movements.  Rather than hit him in the face, I struck him across one arm, so the gun made contact with both his forearm, where the hook-hand started, and his bicep.  My hope was that it would limit his range of movement.



Tattletale, Weld and I hurried to back away as he began to climb to his feet, Tattletale recovering her lightning gun.   I could see her debate striking him again, but she seemed to decide it would be better to keep her distance and hold on to it.



I could see Shadow Stalker materialize behind Weld, with Bitch approaching from the other end of the hallway.  One of the dogs, the setter whose name I couldn't quite remember, had climbed to her feet to join Bitch.  Grue was still out of action.



Weld started laughing, the noise just a little off, coming from someone who I suspected didn't even have to breathe.



Tattletale caught some meaning in his laughter a second before Regent did.  Tattletale, Regent and Shadow Stalker all simultaneously turned toward the front of the building.  Regent and his puppet uttered a whispered ``\emph{Oh shit}'' in unison.



The floodwater and moisture were stirred into an whirlwind flurry around the metal frame by turbines and jets, pushing water and debris a distance away as it set down.  As the engines turned off, the water slopped back into place, lapping around four metal legs.



It was squat, the frame low to the ground, with a snakelike head, and a segmented, sinous body.  It had four legs and a long tail that trailed on the ground in a zig-zagging shape, segmented much as the body had been.  It would have been intimidating enough on its own, but the four engines that were mounted on its upper body, extending out of each of its shoulders in two places, were some combination of a weapons array and a propulsion system.  They bristled with turrets and missiles.  It opened its mouth briefly to vent off some vapor and I could see more weapons contained within.  Foremost among them was some kind of massive cannon.



That explained why Dragon had been so quiet.  When she'd talked about reinforcements, Dragon had been talking about \emph{herself.}



``Okay,'' Tattletale spoke as she backed up, moving her gun to point it at Weld, then Dragon and then back to Weld again.  ``Good news, that's a model Dragon designed for speed, meant to get places \emph{fast}.  Like, say, if she wanted to get an armored suit from Toronto to Brockton Bay to personally take a hand in dealing with a group of teenage villains.  It's not really that serious a combat model.''



I looked at the weapons that bristled from Dragon's shoulders.  If I didn't know Tattletale's power, I wasn't sure I'd believe her.



``Well, that's good,'' Regent replied, ``Except it can still totally kick our asses.''



Tattletale didn't disagree.  ``Best tinker in the world?  Probably.''



I glanced behind us, where Weld was standing with excruciating slowness.  He was already cooling off.  The dog by Bitch's side was growling, now.



Tattletale continued, ``The bad news is that the Protectorate is about a minute away, Grue's still out of action, and there's pretty much no chance we're going to get out of here before then.''





