





The four engines mounted on the shoulders of Dragon's armor shifted position, each aiming at a different point within the lobby.  Tattletale was the first of us to turn and run, the rest of us moving to follow as Dragon opened fire.



All in all, Dragon unloaded four streams of containment foam into the lobby, each of the shoulder mounted turrets  gushing like firehoses.  Only flecks of the spray struck us, but they expanded into blobs of foam the size of golf balls and softballs.  Each blob was tacky, sticky, and any attempt to wipe it away just smeared it and exposed more surface area to the air, making it expand more.



If we'd started running a fraction of a second later, we might have been screwed.



Weld moved to block our retreat, but Shadow Stalker stepped up to fight him with one of the dogs, Bentley, joining her.  It made for a pretty effective combination, as Weld couldn't swing hard enough to hurt the dog without risking hurting his teammate.  The way Regent was having Shadow Stalker fight, there was no self preservation or defense, which worked out to being a more effective combat style than anything else, in its own way.  I was pretty sure Weld had never fought someone who was actively \emph{trying} to get hit.



I'd been drawing my bugs closer to the building since we arrived, and I brought them into the fray as Dragon continued to lock down the lobby with the spray.  The first tactic I tried was blocking the spray with the bugs.  I didn't intend to stop the spray, exactly, but I hoped that I could cause the bugs to catch it & drop down atop Dragon, sticking to her.  It didn't work – the spray was too strong, and the bugs were blasted much too far away.  Only one or two landed on her, and even then, I doubted the positions were that ideal.



Instead, I adjusted my tactics.  The idea was the same, but I didn't want to sacrifice bugs for the purpose of clogging her systems or blocking her guns if it would be that ineffective.  I gathered some bugs on anything that looked like a sensor – glass panes or openings in the armored vehicle, and I set the rest to gathering on the shattered glass that littered the floor of the lobby.  The feet of the insects and arachnids had setae, or small hairs, which branched further into setules.  These fibers, in turn, harnessed Van der Waals forces to cling even to surfaces as slick as glass.



I'd been reading up.



I didn't use this grip to stick to the surface, but instead employed it to collectively lift and pick up the glass.  Six or seven bugs could lift a decent-sized piece of glass if they were on the ground, while anywhere from twelve to thirty could fly with one if I managed it right.



I had a few hundred to employ, with more still arriving.



With this glass, I did my best to catch and block the outlying flecks and drips of spray as it flew through the air, at the periphery of the streams.



The spray knocked some pieces of glass from the air, and struck some bugs, causing the group to lose their collective grip and drop the glass.  That was to be expected.  Others, though, caught the foam on one of the flat panes of the glass.  As more bugs rose with the glass between them, I organized them into loose walls and barriers, to maximize the area they were catching and to overlap so that less bugs were exposed to incoming spray.



``She's got a disadvantage,'' Tattletale spoke, her voice low, ``This suit is meant to fly to serious crises at a moment's notice, deal with dangerous foes.  She's packing too many lethal weapons.''



``That's a \emph{disadvantage}?'' Regent asked.



``She's not about to kill us.  Bad PR, especially for a notable hero traveling into another country to fight virtual unknowns like us.  So we only have to worry about her nonlethal weaponry, and she doesn't have many.''



I nodded acknowledgement, but my focus was elsewhere.  As I judged that enough bugs had caught the foam on one pane of their individual pieces of glass, I directed them to carry the glass down to Dragon.  As I positioned the bugs, the glass stuck to lenses, vents of hot air, vents where air was rushing in, and the smaller joints near segmented areas.



Dragon didn't seem to notice or care.



``Can she see me?'' Imp asked.



Tattletale started to speak, but stopped when one of the streams changed direction to spray closer to us, forcing us to retreat in a hurry.  I glanced at the gift shop.  Would it be a good idea to retreat in there?  The walls were glass, which was both good and bad in that both Dragon and our group could break through it.  The problem was that we risked being trapped if we headed in there.



``No way she got here this fast,'' Tattletale spoke, ``She's based in British Columbia, on the other side of the continent.  This has to be remotely controlled, like the one she used to fight Leviathan, which means the only eyes on you are digital, and--''



``She's not,'' Regent interrupted.



``What?'' Tattletale asked him.



``There's someone in there, I tried using my power on her, experimenting, and I felt some kind of nervous system.  Too much material between me and it for me to do anything with it, and I wouldn't really try it while I'm controlling Shadow Stalker anyways.  I'd probably backfire.''



Shadow Stalker was still fighting Weld.  As Dragon turned a stream toward them, Weld reacted fast enough that I suspected he had some line of communication to her.  He backed out of the way, and Shadow Stalker and the dog both moved in the other direction, with a stream splashing where they had been brawling a second before, blossoming into a pile of foam as tall as they were, separating the two groups of combatants.



Most of my first wave of bugs had either been shot out of the sky by errant bits of spray or had placed their initial pieces of glass and were going back for more.  This wasn't a K.O. hit, and Dragon was too good to let something this minor stop her, however it might delay or hamper her.  The real issue was that this was too slow, and we were on a tight time limit.  Less than a minute, and the Protectorate would arrive.  Their team was smaller with recent deaths and Armsmaster's `retirement', and I hadn't heard about any new recruits.



Then again, I hadn't heard about the \emph{Ward's} new recruits, and here Weld was, being annoyingly persistent.  I was assuming he was the new leader, given his tone with Shadow Stalker.  I wondered if being ridiculously tenacious was a job requirement for being in charge of the Wards.  It made sense to have a commander who wouldn't be removed from the field by an errant attack.  You wanted someone who would stay in the thick of it for the whole fight.



The gift shop jutted out from the wall of the lobby some, the glass panes arranged to showcase more of the pictures, action figures and memorabilia with three broad windows than they might with one.  This layout gave us some cover from Dragon's attacks.  Even when the force of the spray served to break the windows, the expansion of the foam at the edges of the frame soon blocked the worst of it off.  If anything, it was closing the windows off.  Only the pane of glass facing us was left unbroken and largely free of foam.



Sensing this, Dragon started to advance further into the lobby.  Her broad, mechanical feet began hissing with vapor, and the goo my ground-borne bugs were hauling towards her began to run, losing its consistency and stickiness.  She set one foot down directly on a pile of foam, and lifted it up again with no difficulty.  It was clear: the foam wouldn't hamper her.



``So she's piloting that thing, then?'' Imp asked.  ``My power works on her?''



``We can't be sure,'' Tattletale spoke, ``Don't risk it.''



Dragon advanced another step, circling our relative cover from the window to spray inches closer to us.  The way it was piling up, there would be no way to go over it, and the route we had available for going around the far end of it was rapidly closing.  We were getting hemmed in, our backs to the wall by the window.



``Imp!'' Tattletale shouted, ``No!''



I looked at her, confused, but I didn't have time to figure it out.  A flare of orange light caught my attention.  Dragon's mouth had opened wide, and she was spewing something like an ignited accelerant into the lobby.  With this fluid, she drew a three-foot wide line of flame onto the lobby floor, stretching from just below her to the stairwell door by the front desk.  She'd cut off our escape route.



Weld leaped into and through the flame, his hook hands swinging wildly.  Some of the accelerant had landed on him, making him burn, but he didn't seem to mind.



He turned ninety degrees and lunged forward in response to something I couldn't see or hear, then swept his hooks out in a frenzied series of blind attacks.  On the third swing I saw Imp duck beneath the attack, then stumble back out of his reach, towards us.



``The fucking fuck!?'' she shouted.



``Dragon \emph{can} see you, you twit, and she's relaying directions to Weld!'' Tattletale shouted at our new member, ``And what the hell were you hoping to accomplish over there!?''



``I could've figured something out,'' Imp pouted.



Tattletale didn't have a response to that.  Instead, she hauled her gun up and then fired a short burst at Weld.  He backed up into the wall of flame, oddly enough, and Tattletale stopped firing.



Two of Dragon's shoulder turrets were now being set to the task of controlling the flame and keeping it from spreading across the lobby, to the front desk or up to the ceiling.   Twin jets of chemical spray kept the fire limited to the areas Dragon wanted it.



``Doesn't she care about property damage?'' I asked.



``She prefers to keep her data secure and pay out of her own pocket for any damage.  Betting this place is slated for some major renovations anyways, given the state of things,'' Tattletale explained.  The foam was inching closer to us as Dragon prowled further into the lobby.



More of my bugs set sticky pieces of glass down on top of lenses and sensors.  That was apparently enough for Dragon, because she stopped spraying the foam altogether and started using the two turrets that weren't dedicated to fire management to deploying the same vapor that shrouded her legs.  It surrounded her, and the work I'd done to stick things to her began to come apart as the foam turned runny.



A wave of darkness swept over her.  Grue was awake, and had formed a loose group with Shadow Stalker and the dogs.  All but one of the dogs were normal sized, now, with no sign or trace of their mutations.



They still faced the hurdle of passing by Weld, but a blast of darkness and an abrupt change of direction faked out the young hero, letting Grue slip by.



``Dragon's here!?'' he shouted, aghast.



``Yeah!  But we got the stuff, had to wait for you!''



``Go through the gift shop, We'll meet you outside!''  He charged right behind the spot where Dragon was still within the cloud of darkness, and out the front door.  Shadow Stalker simply passed through Weld and bolted for the door, running faster than the Ward's leader could, while the smallest dogs stayed just out of his reach, bolting after Grue.  Bentley, the only dog currently under the effects of Bitch's power, a little beaten and battered, came running towards us, far, far too eager for something that large and strong.



Bitch grabbed his collar before he could leap up to greet her, redirected his momentum, then wrenched him toward the window.  ``Go!'' she shouted, pointing.



Bentley eagerly plowed through the remaining display window, knocking over DVD racks as he landed in the shop.  We followed him in.



The shop had everything cape related, from movies showcasing individual members of the teams to books, magazines, figurines, toys and posters.  The layout of the shop made it awkward as a battlefield.  The shelves, racks, stands and display cases forced visitors into a winding path as they navigated the shop.



The window looking out on the street was smaller than the display windows, and was covered by metal bars.  Tattletale began unloading the lightning cannon on the bars.



Dragon lunged out of the darkness, then spotted us, her shoulder turrets orienting in our direction.  We ducked behind a heavy wooden magazine stand filled with cape magazines and tourism pamphlets as Dragon opened fire with two streams of containment foam.



Tattletale maintained the electrical assault on the bars even as she joined us in taking cover with her back to the magazine stand.  The gun she was holding began to whine, with a pitch so high I could barely hear it.  Bentley reacted, though, turning his head one way, and then the other.  It made Bitch's job of holding his collar and ensuring he stayed behind cover twice as difficult.



The bolts holding the bars to the window frame melted before the bars themselves did.  One side swung free, then the entire assembly dropped down on top of a bookshelf.



The entire room shuddered as Dragon forced her way through the display window.  One gigantic metal talon slammed down on the bookshelf, annihilating most of our cover, and we scrambled to find shelter behind the remaining stands.  Her back legs began working their way towards us, the front of her body staying stationary.  This made her back arch, and her head and shoulder mounted turrets gradually shifted to point downward.  It would be seconds before she was spraying the foam down from directly above us.



The whine of Tattletale's gun reached a crescendo, and a blindingly bright arc of electricity flew from the side of the barrel to skip along the floor.  I worried it would ignite something, but it winked out before it could.



Tattletale lunged for the shelf next to the magazines, grabbing a head-and-torso model of Miss Militia.  She jammed it in between the trigger and the trigger guard of her gun, forcing the trigger into a depressed position.  Then she lobbed the setup over the back of the shattered bookshelf.  The lightning licked the wall and the ceiling before the gun crashed to the floor.  Dragon lurched back to get away from it.



``Go!'' Tattletale shouted, setting her feet below her, then leaping between the twin streams of foam that Dragon turned toward us.  She came only an inch shy of making contact with the heap of foam that Dragon had created.



Dragon heaved herself over and beyond the electrical surge the gun was still pumping out, chasing Tattletale, swiping with one mechanical claw.  I got the sense she was pulling her punches to avoid murdering my teammate, because the attack was slow.  Tattletale slipped past, stepping onto the bookshelf to clear the window.  Or maybe it had something to do with the bugs I had gathered on her sensors.



With Tattletale's escape, Bitch, Imp, Regent, and I were left in the gift shop.  Dragon's lunge for Tattletale had put her directly in our path to the window, and an uneven pile of containment foam surrounded her, in the middle of the room.



Regent and Imp made a break for it.  Imp ducked around to the left, coming within a hair of being caught by the spray Dragon turned her way, then used the cover of the bookshelves to stay out of the line of fire as she ran for the window.  Dragon half-turned away from the rest of us in pursuit.  Regent moved as if he were going to try to move beneath Dragon using the distraction Imp had provided, clearly intending to step on her metal foot.  He changed his mind when a crackle of visible electricity flashed down the mechanical limb.  He turned a hard right, picking up a piece of bookshelf, and used the wood to block the majority of the spray as he passed beneath one of the stray streams.  From there, much as Imp had, he had a clear route.



Dragon moved to bar more of the window with the bulk of her body, her back arching.  Her upper body and head now pointed almost down at an angle, the streams from her shoulders reorienting to block off the escape routes available to Bitch, her dog and me.



So I did something risky and borderline stupid.  I lunged forward and stepped onto the metal foot of Dragon's armored suit, like Regent had been planning to do until he discovered it was electrified.



I had known the same spider silk I'd used for my costume was insulated against electrical charges, had even put that into practice in my fight against Armsmaster during the fundraiser.  This was something altogether different.



I could feel the faint tendrils of electricity snake over the surface of my body, though I only stepped on the metal foot once.  I couldn't tell if the source of the electricity was the gun Tattletale had rigged and thrown – Dragon's tail was close enough to it for the electricity to flow to her – or if it was from Dragon's body itself.



Though the footing was unsteady, I was careful not to touch the metal leg with my upper body, and even turned my head away, risking throwing myself off balance, so my hair wouldn't make contact with it.  As I understood it, the biggest danger the electricity posed was that my body would become part of a circuit.  If the circuit included vital organs, I'd be a goner, and that kind of closed circuit could happen if the electricity could run from my hand and through my heart on the way to my foot.



The gamble and assumption I was working with was that electricity followed the path of least resistance.  Insulated costume vs. vapor in the air?  It would travel through the vapor.  Insulated costume vs. metal leg?  It would travel down the leg.



Either way, I was glad when I didn't burn my foot or have it get fried or go numb.  I was \emph{damn} glad I didn't die.



With all of this consuming my attention, I was caught off guard when something large brushed against me while I was mid-leap.



The impact threw my airborne momentum off, drove me to one side.  My first, most immediate, thought, before I even considered the source of the attack, was where I was about to land.  It was reflexive, but I sent a spray of bugs out from the armor near my glove, scattering them onto the area just in front of me.



Before I had even figured out what my bugs were sensing, I reacted to their signals.  I slammed my arm out, rigid, my hand splayed, and felt a jarring pain as I tried to absorb my entire body weight with one arm and force myself away.  I felt a lack of traction as my hand made contact with something soft and squishy.  My maneuver was too minor to make a real difference, but I managed to buy myself a precious few inches.



My hand, arm and shoulder were caught in the containment foam.



I tried to raise myself to see Dragon looming above, but the foam offered only a rubbery resistance.  It had set with the contact, bonded to my costume.  I was pinned face down on the ground.



What I \emph{did} see, as I raised my head as high as I was able?  Bitch was astride Bentley, who'd grown large enough to ride, and they were standing near the window leading into the street.  I could only see her eyes behind the plastic of her mask, and everything else was communicated through her bearing, her posture, the angle of her head.  I'd seen something similar when I'd first met her.



It hadn't been Dragon that knocked me into the foam.



Dragon turned her upper body to strike at Bitch.  As she moved, her back leg was close enough that some of the vapor was getting on me, slowly liquefying the foam.  It was too slow to matter.  Dragon had me.



Her stainless steel jaws snapped for Bentley, but the dog was already slipping out the window.  Bitch had dismounted and was running to one side, heading off in a different direction to exit at the far end of the window.



Which left me in the gift shop with Dragon.



``I have a sworn responsibility to protect that data,'' she said as she turned her attention to me.  She sounded surprisingly normal.  Her voice was clearly digitized, but it was still too human to match the massive metal frame.



``Can't help you there.  One of my teammates has it.''



``Where are they taking it?''



I stayed silent.



``Your teammates left you behind.  I've read the file on what happened after the Endbringer attack.  Hard feelings?''



``Something like that.''



``If they aren't going to be loyal to you, why protect them?''



Because someone else was depending on it.  But I wasn't going to say that out loud.



The whine of the lightning gun increased by an octave.  I saw Dragon's upper body shift in reaction.



``Move the insects away from my suit, now,'' Dragon ordered me.



``Why would I--''



``Now,'' she ordered, and there was an urgency in her tone that banished any suspicion on my part that there was a ruse or that somehow it might serve my interest to disobey.  I withdrew my bugs, but I kept them poised to return if needed.



Dragon moved back, and her body coiled around the spot where the gun had fallen, segments meeting to loosely interconnect with one another, forming a dome-shaped encasement.  Two shoulder turrets began dispensing foam directly downward, into the dome.



``Count yourself fortunate, Skitter.  I've never killed a criminal without explicit permission and all the filed paperwork, and I'm not about to start with you.  I'll be in contact.''



``What?''  I had to raise my voice to be heard over the high pitched whine.  I couldn't figure out what she meant.



``Think about what I said.  Take a close look at those priorities of yours.''



The vapor had melted enough foam that I could pull myself free and stand.  I got five paces away before the whine ceased.  A second later, lightning began to spill from the gun in overtime.  Dragon's body served to block the vast majority of it, but a few arcs slipped through the cracks in her body.



The full meaning of her words struck me the moment the gun detonated.  A large portion of her suit was destroyed, as was one of the limbs.  Dragon fell to one side.



She'd saved me?



Regent had said Dragon was inside, piloting it, hadn't he?  I stepped closer, trying to see if she was okay.



Regent was right.  There was someone – something – in the suit of armor.



It looked like a fetus, the features were crude, barely humanoid in any sense of the word.  The eyes were half-formed, and it had no nose, only a beak-like mouth.  The head was half-again as large as the body below the neck.  Wires wove in and out of orifices.



It turned to look at me, then made a low mewling sound.  The metal around it began to glow red-hot, then white-hot.  Burns consumed the thing and the flesh changed to a charred black texture as the metal of the frame began to melt and dissolve.  Whatever had happened with the Dragonslayers, it seemed Dragon was dedicated to eliminating all traces of her work when her suits were damaged.



But was that \emph{Dragon}?



No.  She'd seemed to know she was sacrificing her suit, but she'd also said she was going to get in contact with me in the future.  I backed away, then ran for the window.



So what the hell had I just seen?



Had that been someone who was physically affected by their powers?  I wasn't even sure if it was human.



I had a growing, uneasy feeling that this wasn't related to powers and trigger events in the conventional sense.  I pushed it out of my mind.  I had something more pressing to focus on.



I set my foot on the bookcase, then stepped up and through the window to exit the building.  I could see the others dispatching two members of the Protectorate.  Tattletale hurried towards me, said something about the explosion, that she thought I'd be out by now.  I barely registered it.  My attention was on one person as I strode forward.



\emph{Bitch}.





