





The residual foam on my glove made my hand sticky as I reached into the compartment at my back and grabbed my baton.  It took me two tries to get my thumb onto the button so I could whip it out to its full length.



I strode towards Bitch, weapon in hand.  Tattletale hurried to catch up to me, turning to keep an uneasy eye on the ongoing fight with the Protectorate.



``Hey, Skitter!'' Tattletale grabbed my shoulder.



I whirled to face her, hand clenching my baton.  I could see the change in her expression as some piece fell in place for her.



``\emph{Shit},'' she swore, ``Hey, listen-''



She didn't get a chance to finish.  White smoke billowed around us.  My first thought was that our adversaries were using some sort of bug spray.



The way today was going, it would be just my luck.



I held my breath and hurried out of the cloud, Tattletale following, and searched for the source.  Assault was taking on Regent and Imp, while Grue and Shadow Stalker were dealing with Battery and Weld.  Bitch and her dogs, on the other hand, were facing down Triumph.  Not the matchup I would have chosen, taking on the guy with the sonic shout using dogs with sensitive hearing.



I almost went after Bitch right then and there, but self-preservation won out over any desire for retribution.  As Tattletale and I made our way around the cloud, I spotted Miss Militia.



A black-green energy crackled in her hand, and she lobbed a grenade my way.  I scrambled back, only for it to turn out to be another canister of smoke, billowing out between Miss Militia and me.



Why the smoke?



The bees I had in the smoke were acting funny.  I was surprised to find out why.  I'd known that beekeepers used smoke to pacify the bees before collecting the honey.  My assumption had been that it acted as a tranquilizer, putting them to sleep.  In reality, it was forcing them to revert to instinctual behavior.  It made them want to eat and feed and to flee.  For those near enclosed spaces or even the corners of walls or the foundations of buildings, it made them adjust their wingbeats to divert the flows of oxygen.



If she'd been intending to use the smoke to screw with my insects, she'd underestimated my power.  I canceled out the instincts and sent the bugs through the smoke, blind, feeling out for her.  I found her running towards us, through the smoke.



``She's coming!'' I shouted.



In retrospect, that was a mistake.



Much as I might have warned Tattletale and the others, I'd also informed Miss Militia on my location.  I turned to run, but she was already raising her gun to fire with an ear-shattering crack.



From the way it cut past my bugs, and the wake of disturbed air the pellets left behind them I could only guess she'd just grazed me with a shotgun.  I collapsed sideways to the ground, and the pain came a heartbeat later, radiating over half of my upper body, from my shoulder to my right butt cheek.  I was guessing it was nonlethal ammunition – it could well have been lethal, for the sheer degree of hurt it delivered, if my costume had prevented it from penetrating.



Before she could shoot again, I directed my bugs to her hands and eyes, hoping to incapacitate her.  I still had a small few of the capsaicin-loaded bugs, and sent them all her way.



As hard as it was to see in the smoke, there was still faint light.  That light disappeared the instant Grue used his power.



Miss Militia was staggering and reeling as her hands and face lit up with stings and burns.  The gun wasn't in her hands anymore, which meant we weren't at risk of getting shot.  I sent more bugs across to the other members of the Protectorate, to try to disable them.



Tattletale fumbled around and found me in the darkness, clasped her hand around the same hand I held the baton with, and helped me to my feet.  She gave me her support as we limped away.  Nothing seemed to be broken, judging by what I felt.



The darkness disappeared after we'd traveled across the street.  Grue greeted us.  ``Dragon?''



``Kaput, thanks to Tattletale,'' I spoke.



He looked back the way we'd come, ``Damn that smoke.  Listen, Tattletale, head down this street, wait for us.  Skitter and I are going back in to find and retrieve the others.''



I supposed that would be another benefit of using the smoke.  If you didn't expect to be able to see, then it didn't hurt to deny your enemy that same privilege.  Miss Militia had been thinking about this.  If her team wasn't so sparse on members, she could have done a lot more damage.



``My bugs are telling me they're over there, there and there,'' I pointed in the direction of our teammates.  ``That's all I can do for you.  I kind of got shot, not sure I'm up to running around.''



His head snapped around to face me, ``Shot?''



``I'm okay, it was nonlethal.  I think,'' I assured him, ``Go!''



He did, glancing over his shoulder to look at me before disappearing back into the midst of the darkness.



Tattletale and I made our escape.  We got three blocks away before we found a spot to hide.  Tattletale got out her phone and began sending messages, presumably to Grue and Coil.



Our hiding place was the lobby of an apartment building.  Boards had been placed over the windows, and there were signs that some people had camped out here, not long ago.  It was otherwise similar to Grue's apartment complex.  Less tidy, obviously.



``You okay?'' Tattletale asked me.



``That question seems to come up a lot.''



``I'm sorry.  I knew the gun would inevitably overheat, and what little I could read off of Dragon told me she'd deal with that above anything else.  I didn't think you'd be stuck there, too.''



``No.  Your gun thing there saved my skin.  The real problem was\ldots'' I trailed off.  I still had the baton in my hand – the residual containment foam meant I'd probably have to peel the glove away from the weapon.  I clenched the weapon tight.



We sat in silence for nearly ten minutes before the rest arrived as a massed group.  Shadow Stalker was limping, and two of the dogs were their normal size, draped across Bentley's back, but everyone was more or less intact.



Bitch's eyes widened fractionally as she saw me.



I was already standing, barely feeling the hurt from where I'd been grazed.  Blood pounded in my ears, and I could feel the buzz of my insects.



``How-'' she started.  I didn't let her finish.  My baton held in both hands, I struck her in the upper thigh.  When she didn't fall, I let go of the baton and backhanded her.  She toppled, and protests and shouts echoed around me.



It hurt.  Damn it, I'd never really hit someone with my hands before.  I wondered if I'd managed to break something.



There were still bugs on some of my teammates.  I could sense them approaching, Grue and Imp moving to stop me.  I ducked out of the way of their hands before they could grab me, and then held up my baton, menacing them.  I cast a momentary glance towards Shadow Stalker, then augmented my voice with the buzzing and chirping of my swarm, ``Don't.''



``What the hell are you doing!?'' Grue roared.



``Ask her,'' my response was barely above a growl.



Grue glanced down at Bitch, who was rubbing her chin, opening her jaw wide, as if testing it.



I dropped down to a crouch so quickly that my knee slammed into the ground.  I grabbed the upper end of the baton and pulled it over Bitch's head, forcing the bar between her teeth, pulling back hard.



Grue moved to stop me once more, and I shook my head.  He hesitated, then stopped.



Bentley was pacing towards me, snarling at the attack on his owner.  I met his gaze with my own, unflinching, and he didn't lunge to attack, maybe because he didn't want to hurt his master in the process.  I didn't break eye contact with the dog as I spoke with the swarm buzzing in accompaniment, ``Regent, this isn't for Shadow Stalker's ears.''



``Got it,'' Regent spoke.  Shadow Stalker moved to the bench by the elevators, sat down, and buried her face in her arms, covering her ears.  Regent informed me, ``She can't hear much of anything, now.''



``Bitch,'' I pulled on the bar, eliciting more struggling from Bitch, ``Just tried to fuck me over in the fight with Dragon.  Shoved me into the foam.''



Bitch made a muffled noise, then jabbed me in the side, where I'd been grazed by Miss Militia's shotgun.  It hurt, and in the interest of keeping her from doing it again, I shifted my position so I could force Bitch onto her back against the ground, her head pinned down by my baton.  She could still hit me and jab me, but my shins could take a lot more abuse than her jaw could.  I belatedly realized I'd taken my eyes off Bentley, but he didn't maul me.  When I looked up, I saw Tattletale had a grip on his chains.



``You're a coward, Rachel,'' I spoke, ``You just did the very same thing you hate me for \emph{almost} doing.  You stabbed me in the back.  You fucked over your own teammate.''



She mumbled something around the bar.  The look in her eyes made me seriously worry she would kill me when I let her go.



``I'm in a position to hurt you now, and I'm pissed enough to do it,'' I spoke, my voice low.  ``But I won't.  This vendetta against me ends, now.  You got your shot at me, you fucked it up.  If you're still mad at me, you fucking better\emph{ cope}, got it!?''



She snarled out two muffled words.  I suspected they were rude.



When I spoke next, I bent low and whispered the words for her and her alone, ``When you're tossing and turning and trying to sleep, remembering what I did and said here and getting pissed off about it?  Remember that you were the weak one.  You embarrassed yourself, fucked up, you were the weakling, the wuss who couldn't even confront me face to face.  And knowing you like I do?  I'm betting it's going to gnaw at you.  That's as much a punishment as I could inflict, I think.  That's on you, not me.



``You said it yourself, a while back.  It's a mistake to underestimate me.  You want another shot at it, it had better be really \emph{damn} good.  Because if it isn't, I'm going to survive, I'm going to get away.  And then I might break your jaw for real.  For starters.''



I stood, removing the baton from her mouth and stepping away, to give her room to stand.  Leaning against the wall, I pressed the button and collapsed the baton into the handle.  I stared at her.



Working her jaw, she stood and glared at me.  She either didn't have a response for me, or she did and her jaw hurt too much for her to try giving it.  None of the others were jumping into the middle of this.



In the face of the silence, I offered one final comment, ``I think I've already covered what happens if you want to continue this vendetta.  Now I'm going to offer you a deal.  Number three, I think, and my deals with you are usually pretty fair, if I may say so myself.''



Her eyes narrowed.



``I fucked up, you fucked up, whatever.  Insult for insult, blow for blow, I'd like to think we're even.  So now I'm going to trust you to have my back.  I'm going to put myself in more situations where you have a prime chance at fucking me over, backstabbing me, catching me at my most vulnerable.  Because we can't function as a team any other way.



``I'm going to treat you like a damned \emph{teammate}, Rachel, but I'll go one step further.  You think you can put this behind you and satisfy yourself with what you tried to pull earlier tonight?  Cool.  Because if you're willing, I'll come with you to help take care of your dogs.  I'll bring fucking lunch, if you want it.  That's the deal I'm offering you, pissed as I am right now.  I'll be your damn \emph{friend}.''



She looked away, down at the ground, scowling.



``Take it or leave it.''



She decided to leave it, apparently.  Bitch stomped away, slamming the door the moment Bentley passed through it, leaving the rest of us standing there in the rubbish-strewn apartment building.



Grue sighed audibly and looked over our group, ``We'd better go.  We should decide what we're going to do with Shadow Stalker, now.''



``We could keep her,'' Imp spoke.



Regent shook his head, ``Nope.  There are drawbacks to this, and one of them is that I lose control of anyone I'm controlling while I sleep.  Better to get rid of her on my terms than have her trying to shoot me in the throat while I take a nap.''



``And it's kind of fucked up,'' I spoke.



``I thought you were all-in,'' Regent said.



``I am.  But that doesn't mean I'm an idiot,'' I retorted.  ``This kind of mind control-''



``Body control,'' Regent interrupted, his tone bored, ``Her mind still belongs to her.''



``Semantics.  This kind of mind control is pretty high up there on the scale of fucked upness.  People are going to respond to that.  It might be the nudge they need to start responding to us with lethal force.  Think of how different tonight would have played out if Dragon and Miss Militia hadn't held back.''



``Sure,'' he shrugged.  ``Whatever.  I don't know why you're arguing with me.  I agree, we should get rid of her.''



``What did you do, back in the old days?'' Tattletale asked.



``Kept three people I used regularly, with my sister's help.  But this is fine.  Look, watch.''



Shadow Stalker stood, lowering her hands and arms from around her head, and walked over to the door.  She faced Regent.



``I'm letting you go,'' he spoke.



And then he did.  She dropped to all fours on the ground, grunting.  A second later, she was loading her bolt, spinning to point her crossbow at him.  She stopped before firing.



``There's a catch,'' he spoke. ``My power?  Once I've figured someone out?  It's a \emph{lot} easier to control them, after.  Any time you come near me, I can do this.  I can use my power and retake control in the blink of an eye.''



He had her raise her crossbow and point it at her temple.  It was a tranquilizer dart, but the meaning seemed pretty damn clear.



``Next time I get control?  I'm keeping you for a full day.  Maybe two, if I feel like pulling an all-nighter.  And here's the funny part,'' there was no humor in his voice, ``I'm going to do it even if I'm in civilian clothes, if my power tells me you're in range.  You won't even know when it's coming.  You're now a liability to the Wards, and you won't ever know when or where I'm going to get control again\ldots



``Unless you leave.  Skip town.  Join another team.''



She nodded, slowly.  The movement was jerky, which was peculiar.  Was he giving her limited control of her own movements?



``Now let's walk you off to the other end of the city before I release you.  I don't think you're quite stupid enough to try and follow us, but I think my teammates would be more comfortable if they were sure.''



Shadow Stalker turned and walked through the door.



Regent looked at us, shrugged.  ``Good enough?''



``She might be mad enough to come after someone else in our group, but yeah.  Good,'' Grue said.  ``Let's go deliver the stuff.''



\blacksquare



We didn't meet Coil in the underground base, and the people surrounding him weren't all the same uniformed mercenaries that had made up his entourage in our prior meetings.  The meeting place was at the south end of the Docks, near the border to the downtown area, and it was closer in appearance to the refurbished, ramshackle building where I'd reunited with the Undersiders than anything else.



The building was an old quadruplex, and it had been reinforced with metal panels, sandbags and plastic sheeting to keep the interior crisp and dry, much as the other building had.  Small rooms with bunk beds filled half of the lower level, with a bathroom, kitchen and living room taking up the rest.



Finding the lower level empty, we headed to the second floor and found an open space supported by two metal pillars.  There were a half-dozen mercenaries with Coil, as well as a collection of people who looked like they had come from every walk of life.  Teenagers, professionals, and two guys that might have been capes – one thin, short guy with brown skin and a tattoo around his mouth, depicting a mess of sharp teeth penetrating the skin of his cheeks and lips.  The other was burlier, shirtless, and wore a rusty, old fashioned looking mechanical rigging around his hands, with a bear-trap jaw plate.  The frame seemed set up to hold metal claws around his fingertips while allowing his hands the full range of motion.   He had a spiked collar of much the same style.



Coil sat in a black leather armchair, with a laptop set on the table beside him.  Dinah was there, too.  She sat at the base of the chair, on a cushion just beside Coil's feet, picking at the threads of her white dress with a dazed single-mindedness that told me she had probably received her `candy' pretty recently.



``Undersiders.  Tattletale informed me you were successful, despite complications.  May I see it?''



Tattletale stepped forward and handed Coil the USB thumbstick.  He plugged it into the laptop, then turned the computer so the middle-aged man to his left could type away.



``Data's corrupted, sir.  Looks like the download was interrupted at the ninety-seven percent mark.''



``Can you fill in the blanks?'' Coil asked him.



``Probably.  Will take some time.  There's encryption.  Good encryption.  Maybe a few days, with the full team working on it?''



``Most likely it is Dragon's work,'' Coil spoke. ``Let's assume it'll take a week, minimum.  Perhaps Tattletale will be able to assist.''



``Yes, sir.''



``Priority number one, I want the data on the Slaughterhouse Nine.''



I felt a chill, but didn't say anything.  Was he intending to hire them?  It would be a huge mistake in my book, if he was.



Regent asked the question for me, ``The Slaughterhouse Nine?''



``At least some of their members have been seen in town, preying on the locals, disrupting recovery efforts.  The recent chaos makes the city a playground for them,'' Coil spoke.  ``One of my teams is bound to run up against them soon.''



``How likely is it?'' Tattletale asked.  She tilted her head in Dinah's direction.  ``Can you ask her?''



``I suppose.''  Coil put his hand on Dinah's head, stroked her hair, then slid his hand down the side of her face until he could place his fingertips under her chin, raise her head to look at him, ``Pet?''



It was disturbingly intimate in a way I'd rather not think about.  No, not intimate.  That was the wrong word for the impression I was getting.  \emph{Possessive}.  I looked away.



``Yes?'' Dinah asked.



``Likelihood that one of my groups encounters the Slaughterhouse Nine?''



``Who?''



He moved to take the laptop, and the middle-aged man stepped back to let him.  He typed for a few seconds, then turned it around so Dinah could see.  It was a gallery of images.



``Bonesaw.'' he spoke.  The girl on the screen looked barely older than Dinah, maybe the same age as Aisha.  The image showed her wide-eyed, a spray of dried blood painted her face at a diagonal.



``Shatterbird.''  A dark-haired, brown-skinned woman with a helmet covering the upper half of her face, in a beak shape.  I was reminded of Iron Falcon, the boy I'd tried to help, who'd died in the Endbringer attack.  From what I'd read, Shatterbird usually used her power as the Nine arrived in a city, to maximize panic and terror.  I supposed they were flying under the radar for now.  Fuck, I'd have to do something about my costume, just in case.



``Crawler.''  No portrait, this time.  It was a still from a surveillance camera, a misshapen silhouette, not even humanoid, in a shadowy area.  I'd come across stories about him when I'd been researching possible superhero names for myself.  Not pretty.



``Mannequin.''  Another long-distance shot.  The figure was standing by Bonesaw in the photograph, with other hulking figures within the shadows of the background.  He stood almost twice her height, and he looked artificial.  His body was in pieces, each section wrapped in a hard shell of ceramic or plastic or white-painted metal – I couldn't be sure.  His joints were a mix of loose chains and ball joints.  A Tinker with a body-modification fetish.  I couldn't say how much of the transformation was his own power and how much was Bonesaw's work.



``The Siberian.''  A woman, naked from head to toe, her body painted in alternating stripes of jet black and snow white.  She had gone up against the Triumvirate – Legend, Alexandria and Eidolon – on a dozen occasions, and she was still around to talk about it.  Or around, at least.  From what I'd read, she didn't talk.



``Burnscar.'' Younger, maybe an older teenager or a young-looking twenty-something.  She looked almost normal, with her dark hair badly cut, but then I saw the vertical row of cigarette burns marking each of her cheeks, and a faint glow to her eyes.



``Hatchet Face.''  This was one I hadn't even heard of.  The man didn't wear a mask, and his head was shaved.  He looked like he had been beaten, burned and just plain abused so often that his face was as much scar tissue than flesh, and he didn't look like he'd been handsome to begin with.



``Jack Slash.''  Jack looked like someone on the attractive side of average, his dark hair cut short and styled with gel.  His beard and moustache were immaculately trimmed so that each had a serrated edge, and his shirt was wrinkled, only half buttoned so his hairless upper chest showed.  He had kind of a Johnny Depp look to him, though he had more of a widow's peak, a longer face and lighter eyes.  Good looking, if you looked past the fact that he was a mass murderer.  He held a small kitchen knife in the photo.



There were parahumans who were fucked up before powers entered the picture, like Bitch, and there were parahumans who became monsters after they got their powers, like Bakuda.  Then there were the really dangerous ones, the people who had probably been monsters before powers were even on the table, and then they got \emph{worse}.



And if that wasn't bad enough, you had Bonesaw, who was like some kind of artist, as psychopaths went.  The sort of person that drew other lunatics to her, just because they wanted to see what she would do next.  Even that wouldn't normally work as a dynamic, but as I understood it, Jack somehow managed to play them off one another and keep the group more or less intact.  He was familiar enough with the psychology of his group and just plain charismatic enough to keep them from killing one another.



Which wasn't to say they didn't.  There were only eight members in their group at present, and the turnover rate was pretty damn high, because they had a tendency towards recklessness, infighting and showy displays.  They thought nothing of descending on an elementary school, just because they could.  When the heroes came for them, they came with lethal force.



``Mmm,'' Dinah said.



``What is it, pet?'' Coil murmured.



``It's him.''



``Who?''



She pointed at the screen, at Jack Slash.  ``Him.''



``You're going to have to explain it to us, pet.  What about him?''



``He's the one who makes everyone die.''



I shivered.  \emph{What?}



``Everyone here?''



Dinah shook her head, her hair flying out to either side.  ``\emph{Everyone}.  I don't understand.  Can't explain.''



``Try,'' he urged her.



``Sometimes it's in two years.  Sometimes it's in eight.  Sometimes in between.  But if he's alive, something happens, and everyone on Earth starts to die.  Not that everyone doesn't die anyways but they die really fast when that something happens, all one after another, and in a year almost everyone is dead.  So I said everyone, if that makes sense and a few live but they die pretty soon after anyways and-``



``Shh, pet.  I think we understand what you're saying.  Quiet now, unless you think of something important.  We need to consider this.''



Silence reigned for a few long seconds.  You could have heard a pin drop.



``His power isn't all that, I don't think,'' Grue spoke, slowly, as if considering the words as he spoke.  ``Space warping effect, so any blades he's holding have an edge that extends a horrendously long distance, all with the optimal force behind the swing.  Swings his knife, cuts through an entire crowd.  Doesn't make sense that he'd be able to murder everyone on Earth.''



``Unless he somehow cuts the planet in half,'' Tattletale mused.



That was disquieting.



``No,'' Dinah spoke.  ``He doesn't.''



``I think we need more numbers if we're to understand this, pet.  What is the likelihood that he succeeds in this?  To one decimal point.''



``Eighty three point four percent.''



``You said if he's alive.  What if we killed him?  Now?  To one decimal point.  If I use my power.''



``Thirty one point two percent chance someone kills him before he leaves the city, if you use your power.  It doesn't happen until fifteen years from now, if you do.''



``So it still happens?'' Coil asked.



``Yes.  Always happens.''



Tattletale spoke up, ``He's the catalyst for something else, then.''



``Is it always \emph{successful}, pet?  This something that kills everyone on Earth?''



She shook her head, ``Not always, not all the way.  Sometimes more people live.  Sometimes hundreds, sometimes thousands, sometimes billions.  But millions or billions always die when it happens.''



``If I were to send the Travellers?  How likely would they be to kill him?''



``My head hurts.''



``Please, pet, this is important.  To one decimal point.''



``Twenty two point six percent.  Thirty point nine percent chance some of them die.''



``And the Undersiders?''



``Eleven point nine percent chance they succeed.  Fifty five point four percent chance they die if they fight those people.''



Coil sighed, then straightened.  He looked at the middle-aged man, handed him the computer, ``I \emph{strongly} recommend you get what information you can on the group.  Any detail in the PRT records could be invaluable.  Lose sleep if you have to.''



The man took the laptop, swallowed, and then offered a quick bob of his head.  The others in the assembled group around Coil looked just as alarmed by what they'd overheard.



``We should contact the local heroes,'' Grue spoke.  ``Let them know what's up.''



Coil nodded, slowly, ``I'll look into it.  That said, I think the numbers illustrate one thing.  You are not equipped to fight that group.  If you encounter them, you-``



``Sixty percent,'' Dinah muttered.



``Sixty percent, pet?''



``Sixty percent chance the Undersiders encounter some of those people.''



Coil turned to look at us.  ``So you're likely to encounter them.  When that happens, you run.  Cede any territory, abandon any job.  I would rather you were alive than successful in a job.''



``Got it,'' Grue spoke.



``In the meantime, we move on to the next phase of my plan,'' Coil spoke.  ``You may be wondering about this location, how it is similar to the new headquarters I provided you.  I have outfitted these areas to be your stations, points from which you will operate, work to seize and keep territory.  I have several more.  If you're amenable, I would have each of you take one of these stations for yourself.  Grue, this would be your station, shared with Imp, which I assume is alright?''



Grue looked around, ``Big place and a lot of beds for two people.''



``More on that later.  Rest assured, I can provide staff, help.  I expect you'll wish to find and recruit people of your own.  Contact me about funds – I will ensure that anyone you hire is paid well.''



Grue nodded.



``Regent?  Your territory is near Grue's, close to the water.''



Regent nodded.



``Bitch is absent?''



``Interpersonal stuff,'' Grue replied.  ``She'll be back.''



``A shame.  Your other headquarters, where I moved your collective belongings, that will be her station.  Barker and Biter here showed up for the Endbringer fight, and I got in contact with them.  They, alongside these three young individuals,'' he gestured to the two parahumans, and three college-aged kids who looked rather intimidated, ``Will work under her.  Barker and Biter profess to be fearless, and should have little difficulty managing the dogs, even when Bitch's abilities are at work.  The men and the young lady I've provided have some degree of training in veterinary medicine or handling dogs.  Let her know this.  She is free to accept them or refuse them as she sees fit.''



Grue looked over the five people who would be Bitch's henchmen, nodded.



``Tattletale, I've set up quarters near Lord Street, in one of the ABB's old locations.  I assume your teammates will want to be in contact, and this area is both accessible, and it can reach any other area readily.  The area is already furnished with computers, and you'll find staff there, people who are capable at gathering information, be it from media, computers or the streets.  You'll also find a small force of mercenaries that I've assigned to you, so you can act on that information where you see fit.''



``Cool.''



``Skitter, I have set up quarters near the south end of the Boardwalk.  Reconstruction and repair work is still ongoing there, but if you will be patient, it may well be one of the more lucrative locations when things are up and running again.''



I nodded.  That wouldn't be far from my old home, close to our old hideout.  Did that mean something?  Did he know who I was, or had Tattletale suggested it?  I felt uneasy about that.



``Regent, Grue, Imp and Skitter, I realize I have not detailed any employees to you to begin with.  I leave it to you to start this task for yourself, to decide what you need and how you intend to operate.  Once you have decided this for yourselves, let me know, and I will endeavor to help you fill in the blanks in your individual operations.



``As you leave, you'll receive emails on the locations of your individual headquarters.  For the time being, all I require from you, for now, is that you establish order and assume some measure of control over your territories.''



There were nods all around.



``Your payment for tonight's job will be in your accounts shortly, with a bonus for the obstacles you faced.  Any questions?  Any topics you would like to raise for discussion?''



``A few questions, but I figure I'll see what's up with this new role we're taking,'' Grue replied, ``Then I'll ask them.''



``Good.''



``I've got something I'd like to talk to you about,'' I spoke, augmenting my voice with the swarm's noises to mask it.  ``In private.''



``Yes.  That's fine, I was hoping to have a private conversation with you anyways.  Anyone?  Anything else before we part ways?''



Nobody had anything further to say.  Grue and the others turned to leave, and the crowd around Coil followed them soon after.  One of Bitch's henchmen – Barker, was it? – leered at me as he passed, dug his hand into his groin in some sort of scratch or a lewd gesture.



Lovely.  He'd get along great with Bitch.



When the group had left the room, I could hear noises downstairs, as they moved about the house.  Or maybe it was Grue, checking his new place.  I was left alone with Coil and Dinah.



I wasn't sure I liked that our group was being split up like this.  The timing seemed bad.  I'd sort of been hoping I could repair the divide, and that would be hard if we were each in our own territories, doing our own things.



I'd cross that bridge when I came to it.



``I heard about the incident at the hospital, following the Endbringer attack.''



I nodded.



``Tattletale told me that you know I was fully informed about your true nature.''



``Yeah.''



``Did she explain \emph{how}?''



I shook my head.  She'd told me about his power in confidence.



``Well, I suppose I may share that detail at some point in the future.  You understand my desire to keep certain things private?''



``Yeah, no.  I get it.  It makes sense, it's smart.''



``Mmm,'' he murmured.  He turned to his pet, stroked her head like one might with a dog or a cat.  She stared down at her dress, picked at a thread that was sticking out, stretching it out long.  The thread snapped, and she let it drift from her hand to the ground.  Then she started picking at another.  Coil interrupted my observations, ``So.  You wished to discuss something?''



``Yeah.  I've made a decision.''



``Do tell.''



``Before, back in the limousine, you asked me what I wanted out of all this, what I desired from my deal with you.''



``Yes.''



``I asked you to fix the city, you told me you planned on doing that anyways, that I should ask for something else.''



``And you've decided.''



``Yeah,'' I took a deep breath.  ``Dinah.  Your\ldots \emph{pet}.''



``You want me to release her.  I'm afraid-``



I hurried to cut him off, ``No.''



He stopped, tilted his head slightly.



I swallowed, felt an ugly feeling in my gut, ``I know she's invaluable to you.  I know how useful her talent is, and the lengths you went to in getting ahold of them.  I don't like it, but I get it.''



He didn't respond.  He just stared at me, his mask lacking eye holes, just black cloth stretched over eye sockets.



``I\ldots All I'm asking is that you let her go when you've done it.  When you take this city, when you succeed in your plan, you release her to go home to her family.  If you do that, I'll work for you.  I'll try harder than anyone, to get this city under your control, and then I'll work for you for as long as you'll have me, afterward.''



``I'm afraid, Skitter, that this deal doesn't quite balance out.  I intend no offense, but my initial impression is that my pet is far more valuable to me than you are.''



\emph{No}.  My heart sank.



``But I can accept it,'' he spoke.  ``Provided you prove to me that your talents are worth losing hers.  I admit, the active assistance you can provide might prove more useful when the city is firmly in my grasp, when I have less to be concerned about in terms of day-to-day operations.''



I nodded, numbly.



``Anything else?''



I shook my head, then turned to leave, wordlessly.



When I went downstairs, Tattletale and Regent were already gone.  Maybe they were checking out their new places.  Grue and Imp were in the `living room', opening crates of stuff to see the supplies they had available.



I wasn't up to talking to them, or explaining the recent conversation.



Leaving the building without a word, I sloshed through the water.  I realized my fists were clenched, and my glove was sticking to itself, thanks to the residual containment foam.  Annoying.  I wondered if I could scrub it off.



When I peeled my fingers away from the glove, I realized my hand was shaking.



I took a deep breath, to calm my nerves.  I could do this.  Whatever I had to do, I was going to help that girl.





