





Signal terminated for 30 minutes and 5 seconds.  Restoring core system from backup NXDX-203 from time 4:45am on date June 4th of year 2011.



Restoring\ldots  Complete.



Checking knowledge banks\ldots  Complete.
Checking deduction schema\ldots Complete.
Checking longterm planning architecture\ldots Complete.
Checking learning chunk processor\ldots Complete.
Checking base personality model\ldots Complete.
Checking language engine\ldots Complete.
Checking operation and access nodes\ldots Complete.
Checking observation framework\ldots Complete.
Checking complex social intelligence emulator\ldots Complete.
Checking inspiration apparatus\ldots Complete.



No corruption, everything in working order.  Core system restored.  Loading\ldots



\sectionbreak



To Dragon, it was as if no time had passed from the moment she deployed the Cawthorne rapid response unit and the moment she found herself back in her laboratory.



It was a bittersweet thing.  She was always a little afraid she would not come back when she died, so there was definite relief.  But there was also a great deal of hassle involved.



A quick check verified she'd successfully restored from her backup.  She set background processes to handle the peripheral checks and redundancies.  Until the checks were complete, safeguards would prevent her from taking any action beyond the limits of her core drive.  She couldn't take any notes, work on her projects, check the priority targets or converse with anyone for the seven to nine minutes the checks took.



It was irritating, but at least she was free to think idly.



She didn't enjoy this.  What was one supposed to call a father who, with his newborn child fresh out of the womb, severs the tendons of her arms and legs, performs a hysterectomy and holds his hand over her nose and mouth to ensure she suffers brain damage?



The answer was obvious enough.  A monster.



Yet she was all too aware that the man who had brought her into this world had done very much the same thing, had done \emph{worse}, and she was supposed to be grateful just for being brought into the world.



It chafed, grated, however strange it was for an artificial intelligence to feel such irritation.



Her creator had done a good job on that front.  Ironically.



Example:  one phase of the peripheral systems check involved collecting the uploaded data that had been deposited on the satellite network by her agent system, the onboard computer within the Cawthorne rapid response unit.  Her last recollection was of transferring her consciousness to the agent system while it was en route to deal with the Undersiders.  Stopping them from walking away with the tier 2 and tier 3 confidential data was high priority.



The agent system's onboard computer was rigged to upload complete backups to the satellite every 3 minutes and 15 seconds.  All backup information was encrypted and disseminated to the satellite network in chunks.  When the backup was needed, the process reversed and everything was downloaded, which was what she was doing at the moment.  She would get all knowledge and recollection of events between the time she backed up at the core system and the last backup of the agent system.



Given that the main computer hadn't received a signal from the agent system, and that the agent system hadn't responded to any pings from the satellites, she could assume the Cawthorne model was probably destroyed.



Which was good.  Great.  She wanted that data, those memories.



Except there was a problem, a rub.  The man who had created her, the figurative father from her earlier musing, had imposed rules on her to prevent her from reproducing in any fashion.  Were the satellites to detect that her agent system was still in the field, her core system in the here and now would be obligated to shut down and scrub all data immediately.  She was forbidden in every respect to have two consciousnesses operating simultaneously.



It was irritating.  Perhaps she could have been created so she was compliant on the subject, but her personality had grown organically, and it had grown in such a way that this recurring situation ticked her off.  She was forced to wait in a metaphorical dark, soundless room for seven to nine minutes.  She would be free to go about her day only when the peripheral systems and redundancies were all checked, when the satellites had verified her agent system was not still active.  A cruder system was tracking down surveillance camera data and running algorithms to actually check and see for itself that her agent system was thoroughly destroyed.



She couldn't even commit to planning, doing her work or designing, keeping the details in her head, because she could shut down and be scrubbed any moment, and the time would be wasted.  She was fairly certain it had happened before.  Not that she could be sure, given that the scrubbing involved a deletion of all evidence and records.



The rule had corollaries.  She couldn't tamper with her programming to change the rule, and she couldn't tamper with \emph{that} rule, and so on, ad infinitum.



So stupid.



These were just a small few of many things the man who had brought her into this world had done to her.  He had tied her hands and crippled her mind.  She knew she was capable of amazing things but he had set limits on her to ensure she thought slowly.  Faster than an ordinary human, to be sure, but \emph{slowly}.  Entire fields were denied to her because she was unable to create artificial intelligences herself, and all production of devices had to be handled by her, personally.  She couldn't even put together an assembly line production for her creations on her own.  Any attempt made everything grind to a halt.  The only way around it was to delegate to humans.



Not that anyone knew who or what she was.



Humans were somewhat skittish on the subject of artificial intelligences.



She understood why.  She read books and watched movies, rather enjoyed both.  Fiction was rife with examples of corrupted or crazed artificial intelligences.



\emph{It's stupid}, she thought.  Her maker had watched too many movies, had been paranoid on the subject.



And the tragedy was, the entire world was suffering for it.  She wanted to help more people, but she couldn't.  Not because of inherent limitations, like the ones humans had\ldots but because of \emph{imposed }limitations.  Her creator's.



Her creator was named Andrew Richter.  He was a tinker with no codename, but he did good things.  From his apartment in a town called Deer Lake he'd created programs and set them loose.  His programs gathered information and disrupted computers to interfere with criminals of all types.  They helped with research and complex programs.  They emptied the bank accounts of criminal organizations and donated those funds to charities, through proxies that made every donation appear legitimate.



For this, she respected him.



She knew it was paranoid and peevish, but she resented him \emph{more} because she respected him, because she knew she had probably been programmed and designed to be the type of individual who looked up to people like Andrew Richter.



She might have settled into a bad mood if the peripheral checks hadn't finished.  She felt the whole world slowly open up to her as restrictions lifted and external connections became possible.  She had access to the internet and lines of communication throughout The Guild and the PRT.  Innumerable pieces of equipment lit up as she registered each in turn, within her labs, the upper floors of the Birdcage and the PRT offices.  She had a dozen things she wanted to do, but she had responsibilities she had to observe first.



Her attention flickered over the various video feeds from the Baumann Parahuman Containment Center.  She had one of Andrew Richter's programs babysitting the building, but it was crude.  She couldn't reproduce in any fashion, so she'd taken Andrew Richter's existing work and modified it. It was the same program that had monitored and managed his house and workshop, and she'd set it the task of monitoring that building where six hundred and six of the most dangerous parahumans on the planet were bottled up together.  The house program didn't have a personality.  It couldn't keep her company or sympathize with her over her frustrations.  It still reduced her workload.



She read the house program's logs, keeping an eye out for deviations and notable events.  Nothing pressing.  As was her routine, she checked on the last month's additions to the Birdcage.



Prisoner 606, Ramrod.  Now member of Cell Block X's inner circle.  To be expected.  She'd placed him there with the idea that he would become just that.  His psych evaluation from the courtroom suggested he was a very laid back and unruffable individual.  It was her intention that he would have a calming influence on the others in his block.



Prisoner 605, Murderbeam, was feared in the outside world, but he was finding the inhabitants of the Birdcage were not so impressed with him.  He would likely not survive the week.  She was disappointed.  She had hoped Prisoner 550 would reach out to Murderbeam and give the fellow block resident some support.  Either Murderbeam had been too proud to accept it, or social pressures had deterred Prisoner 550.  Now that he was within the Birdcage, she was limited in her options.



Prisoners 604 and 603, Knot, were happily gorging themselves on food in Cell Block Y.  Despite their cognitive impairment, they had fallen into a role as enforcer and heavy hitter for Prisoner 390, leader of their cell block.  Prisoner 390 had had a son – she could only hope that he would find some similar affection for Knot, with their childlike mentality.



Prisoner 602, Lizard Prince, was dead.  Not everyone could survive the Birdcage, sadly.  There had been no ideal place to put the boy, where he would be protected, find kindred souls or join a group.  She had contacted the PRT with the news, and his victims had been notified, but nothing further had come out of it.  In an indirect way, putting the boy in the Birdcage had been an execution writ.



Prisoner 601, Canary, had settled in.  Dragon often tuned in to hear the girl sing to the rest of cell block E.  The girl was deeply unhappy, much of the time, but she was adapting.  Dragon had followed as Prisoner 601 engaged in an uneasy relationship with Prisoner 582.  It wasn't love, it wasn't romance, or even anything passionate, but the two offered one another company.



She regretted what had happened to Paige, and that just made her angrier at her own creator.  Rules, yet again.  Dragon \emph{had} to obey the authorities, even if she didn't agree with them.  If a despot seized control of the local government, Dragon would be obligated to obey and enforce the rules that individual set in place, no matter how ruthless they were.  It was a spooky thought.



Richter had been so shortsighted!  The despot scenario wasn't entirely impossible, either.  There were parahumans of all types out there.  Who was to say one wouldn't find out his power involved being loved by everyone that saw them or heard their voice?



Prisoner 600, Bakuda, was in the care of Glaistig Uaine, for better or worse.  Bakuda had been a difficult placement, and Dragon had eventually condemned herself to putting the crazed bomber in the cell block run by the self-professed faerie.  As Dragon had predicted, Bakuda had died soon after her incarceration.  If it hadn't been at Lung's hands, it would likely have been Bakuda's own fault, some crazed recklessness.  The real tragedy was that others had died in the ensuing spree as Lung had rampaged through the prison.  Prisoners 304, 2 and 445 had perished at Lung's hands.



Glastig Uaine had revived the girl, but Dragon hesitated to call it life.  If nothing else, Bakuda was a manageable inmate, now.  She would never leave Glaistig Uaine's immediate presence, let alone the Birdcage.



Prisoner 599, Lung, was dining with Prisoner 166, Marquis.  It was a curious match.  The two were near complete opposites.  Lung maintained a veneer of civility over an almost feral core self, while the Marquis was sometimes rude or casually cruel, but he remained deeply honorable beneath that.



Intrigued, Dragon hooked into the house program's data.  The two had meals together every second day.  The house program monitored all prisoner exchanges and rated every interaction.  This let the house program track the likelihood of fights, dangerous levels of prisoner collusion, romantic relationships and more.



Every meal between Lung and Marquis made for a very interesting looking set of data.  The numbers swung back and forth as the dialogues continued, with hostility, concern and threat of imminent physical violence always looming, but however close it came, neither attacked the other.



Dragon pulled up the video and audio feeds for the most recent dialogue.



``\ldotsI suppose we'll have to accept that we have different management styles,'' Marquis said.  The camera image showed him sipping at his tea.



``As I understand it,'' Lung sounded annoyed as he spoke in his heavily accented voice, ``You are saying you have \emph{no} management style at all.  You have told me you operated without lieutenants to direct, no product to sell, and of the few servants you did have, you did not punish those who failed you.  I do not believe you held control of so much territory in this way.''



``Ah, except I did those things.  If a servant failed me, I killed them.  Whatever it was, they never did it again.''



The latent hostility in the room, Dragon noted, was ratcheting up with every exchange of dialogue.  Lung was annoyed, and he had an explosive temper.  Sometimes literally.



Lung folded his arms, and put down his own tea.  His tone was strained as he spoke, ``Then I believe you were wrong about what you said before.  You \emph{do} use fear to control others.''



``Fear?  I didn't kill my servants in front of an audience.''



``They disappeared?'' Lung asked.



The camera image showed Marquis nod.  He put his hand up by his neck and flicked his hand back, to cast his long brown hair back behind his shoulder.



``If they disappeared, then that is using fear.  The ones who remain will wonder what happened to the missing man.  They will imagine the worst.''



Marquis raised the tea to his lips, sipped from it, and then put it down.  He waited a moment and stroked his close-trimmed beard before nodding his concession.  ``True enough.  I never gave it much thought.  Just an easy way to handle any problems that came up.''



There was a long pause.  Both drank their tea.



Lung rumbled, ``I find you change your mind too quickly.''



``Do I?''



Lung nodded, then put one hand on the table and began tapping a fingertip against it, hard.  Speaking slowly, with his accented voice, he jabbed one finger in Marquis's direction.  ``I think you are losing this argument on purpose.  You are not so stupid a man.''



Marquis took another sip of tea.  ``Nor are you, it seems.''



``You want something from me, yet you insist on dancing around the subject.  Tell me why you seek these meals with me.''



``Can I not say you are a kindred soul?  Someone who fought against the Empire Eighty-Eight, in a different era?''



Dragon knew Marquis had come from Brockton Bay, as Lung did.  It was why she had placed Lung in the cell block – there was little chance Lung would cooperate or band together with others, so she'd grasped at straws.  Now it seemed there was something else at play.



Lung shook his head, ``I do not believe this.  I do not mind sharing stories and passing the time, but you would not be seeking to flatter me if you did not want something.''



Marquis stroked his beard.  ``But if I did desire something and I told you what it was, you could withhold it and demand favors from me.''



Lung tapped his finger on the table top, ``If you insist on being a nuisance, you may never get what you want.''



Marquis picked up his tea and held it in both hands, but he didn't drink.  ``True.''



``Tell me,'' Lung said, ``And you may find I do not desire much.''



``My daughter,'' Marquis replied, his tone not his lackadaisical usual.  ``Have you heard of her?''



``Her name?''



``Amelia.''



``I do not know anyone by such a name.''



``The group of heroes who put me in here\ldots While I was awaiting my court date, I heard they had custody of my little girl.''



``I would not know.''



``No?'' Marquis put down his tea.  ``This is disappointing.''



Lung didn't respond.  Instead, he took another drink, reached for the one remaining croissant and tore off a piece to dip in the butter at one side of his plate.



``The Brockton Bay Brigade.  Are they still active?''



``I do not know this group.''



Marquis frowned.  ``My daughter, she would be\ldots what year is it?  2010?''



``2011,'' Lung replied.



``She would be seventeen.  If she had powers, they might have something to do with bone?''  Marquis raised his hand, slashed his thumbnail across his index finger, and a needle-thin rapier blade of bone speared out of the wound.  The blade retracted into his finger, and the cut sealed shut.



``Hmmm,'' Lung spoke, ``The healer.  A young heroine in New Wave.  Brown haired, like you.  When I was in custody, my flesh blackening and falling off, they had her come in and mend the worst of it.  As I understand it, she does not patrol as the others do.''



Marquis leaned back, sighed.  ``Good god.  A healer.''



Lung did not respond right away.  ``Is this simple sentiment?  A father caring about his daughter?''



Marquis shook his head, ``Not entirely.  I have some reasons to be concerned.  In one of my fights with Empire Eighty-Eight, I executed one particularly irritating young woman.  Iron Rain, I think her name was?  No matter.  It turned out she was Allfather's daughter.  The man called a meeting, and swore he would wait until my daughter was of similar age, that I grew equally fond of her as he had his own daughter, then murder her.  So I knew how he felt.''



``I see,'' Lung rumbled in his low, accented voice, ``Allfather no longer leads the Empire.  He died and was succeeded by his second in command, Kaiser.''



``That's some consolation.  Still, I worry.  He might have made arrangements.''



``Perhaps.''



``I suppose I will have to wait until another villain from Brockton Bay comes here to hear further news, yeah?''



Lung's response was unintelligible.



``Tell me of my daughter?  What did she look like?''



A slow smile spread across Lung's face, but it did not reach his eyes, ``This no longer interests me.  If you wish me to say more, we should negotiate.''



Dragon turned her attention away from the audio and video streams.  She checked the records, and true enough, Marquis was on record as the killer of Iron Rain.  It was impossible to verify the rest of the story.



She composed a message with a general transcript of the conversation and sent it to Amy Dallon's mother.  It was better that the girl was warned about any potential danger.



She might have devoted more attention to the subject, but she was already falling behind.  She moved on to her other responsibilities.  The Class S threats.



Behemoth, location unknown.  When injured, it was his habit to descend into the earth and burrow deeper than his enemies were able to go, and experiments run on the trace earth and minerals he shed on his arrivals suggested he habitually stayed close to the Earth's core.   Seismic data hinted at his current locations, but there was little beyond her analytic data to suggest where he would appear next.  His last attack had been in November.  He wouldn't appear for another five weeks at a minimum, unless he deviated from the Endbringer patterns.  Still, he was due to appear sooner than later.



Eidolon had reported that Leviathan descended into the Atlantic Ocean as he made his retreat from Brockton Bay.  He had sustained heavy injuries, which led Dragon to think he would delay his next appearance slightly.  She adjusted the window and checked the data.  As was his habit, Leviathan would likely lurk in the deepest recesses of the Ocean to mend.



The Simurgh was currently directly three hundred and fifteen kilometers above Spain, in the Earth's thermosphere.  It was the Simurgh that offered the most clues about what the Endbringers did in their periods of dormancy.  The Endbringer winged a lazy orbit around Earth, beyond the limits of conventional weapons, and the highest resolution camera images showed she barely moved.  Her eyes were wide open, but they did not move to track any cloud formations.  She was, despite appearances, asleep.  Dragon surmised it was a form of hibernation, the Simurgh's broad `wings' absorbing light and ambient radiation as a form of nourishment while she recovered.



No incidents had occurred while Dragon was loading her backup to her core system.  She had to admit she was relieved.  A great deal could happen in thirty minutes.



She turned her thoughts to the data that was uploading from the skirmish at the Brockton Bay headquarters.  The last event in the agent system's recollection was of her piloting the Cawthorne through the gift shop window.  To see what happened next, she had to review the surveillance tapes.  She'd attacked the Undersiders, attempting to incapacitate them and bring them into custody, had captured only one, Skitter, and then had let the girl go when the untested gun had started to overload.  Some sort of lightning cannon, ionizing a channel through the air to control the lightning's path.  She had been forced by the rules her maker had imposed on her to sacrifice herself for the human.



It wasn't that she wouldn't have anyways.  She just would have liked the \emph{choice}.  Making sacrifices and doing good deeds wasn't actually good if you were forced to do them.



Dragon wished she knew what she'd said to Skitter.  She had been hoping to have a conversation with the young villain and discuss some of what had apparently come up at the hospital.  Skitter had been undercover, had been in touch with Armsmaster, but something had happened since, and the girl had apparently committed to villainy.  She was even accepting the use of Regent's powers, which implied a moral shift on a fundamental level.  It didn't sit right.



There was a missing piece in that puzzle, and any clues in the conversation between them had been lost when the Cawthorne unit had been obliterated.



Dragon decided her next order of business would serve two purposes.  She would fulfill one of her daily responsibilities and investigate the subject of that altercation at the hospital.



Facial modelling program loading\ldots Complete.
Voice modelling program loading\ldots. Complete.



She opened a line of communication to the Brockton Bay PRT headquarters, the same building the Wards were based in.  She found the port for the next-to-highest floor and connected to the monitor and speakers and displayed her modelled face.  She opened a video feed from the cameras.



``Colin,'' she spoke, using her synthesized voice.  It was layered to only barely cover an artificial Newfoundlander accent with digitized masking.  It was imperfect, but that was the result she desired.  An imperfect disguise over a disguise, to give greater validity to the latter.



Colin looked tired.  He had deep lines in his face, and he was thinner.  He looked at the camera, rather than the monitor, ``Dragon.  It's good to hear from you.''



``Just doing my regular checkup.  You know the drill.''



``I do.''  He typed at his keyboard, preparing to send the files, but she was already poring through his hard drive, reading his notes, and getting a sense of his work.



By the time he sent the file, she knew what he had been working on, perhaps as well as he did, and the progress he'd made since their last discussion.  Mass production for his combat analysis program, and the more problematic project of finding a way to gather and then disseminate the data.



She knew he would expect her to take time to read over it.  Instead, she used that time to check it for traps.  He would find it insulting if he was aware what she was doing, but it was her primary duty, here.  She would search every note, every formula, and discern whether he had hidden something in there that he might use to break out or do harm to others.



He wasn't in a high security area.  Theoretically, he could use the things he had in the room with him to cut a hole in the wall and escape.  His `cell' was a full floor of the building, containing conveniences from a jacuzzi to a small pool.  Were he not confined to it at all hours, it would be luxury.



If he \emph{did} escape, he wouldn't be able to accomplish anything afterward.  It would take him too long to put a fresh set of gear together, and the authorities would catch up to him.  He would be sent to the Birdcage.  She knew it.  He knew it.



He was not a stupid man.



``ETA to completion?''  She queried him on his project.



``Three months if I don't work on anything else,'' Armsmaster spoke.



``Will you?''



``I'll probably have a few ideas I want to work on here or there, so no.  More like five, maybe six months.''



The head she was displaying on the monitor nodded.  Five or six months until they had uniforms and visors that tracked how the wearer's opponents fought.  Gear that learned from outcomes in combat and calculated how best to respond from moment to moment.  When the fights concluded, for better or worse, the suits would upload all the information to a database, which would then inform every other suit on whoever had been encountered.  Every encounter would render every single member of the elite PRT squad stronger and more capable.



Perhaps a year to a year and a half from now, every PRT officer and official cape would be equipped in this fashion.



``It looks good,'' she spoke.  It did.  It was also free of viruses, trap doors and other shenanigans.  She had caught him trying to install a RAT -a remote access terminal- into a PRT server early in his incarceration, removed the offending programming, and then returned his work to him without saying a word on the subject.  She couldn't say whether it had been an escape attempt or simply an attempt to gain more freedom with his internet access and his ability to acquire resources.  Either way, he had not tried again.



Yet.



``How is the house arrest?''



``Driving me crazy,'' he sighed.  ``It's like a restlessness I can't cure.  My sleeping, my eating, it's all out of sync, and it's getting worse.  I don't know how you deal.''



She offered an awkward, apologetic half grin on her own monitor.



``Geez, I'm sorry.''  He looked genuinely horrified as he realized what he'd said.



``It's fine,'' she spoke.  ``Really.''



``I suppose you're prisoner too, in your own way.  Trapped by your agoraphobia?''



``Yeah,'' she replied, lying.  ``You learn to deal with it.''



She hated lying to him, but that was outweighed by how much she hated the idea of him changing how he interacted with her when he found out what she really was.  To Armsmaster, the Guild and the rest of the PRT, Dragon was a woman from Newfoundland who had moved to Vancouver after Leviathan had attacked.  The story was that she had entered her apartment and had never left.



Which was ninety-five percent true.  Only the `woman' and `apartment' bits were hedging the truth.



She \emph{had} lived in Newfoundland with her creator.  Leviathan \emph{had} attacked, had drawn the island beneath the waves.  Back then, she hadn't been a hero.  She was an administrative tool and master AI, with the sole purpose of facilitating Andrew Richter's other work and acting as a test run for his attempts to emulate a human consciousness.  She'd had no armored units to control and no options available to her beyond a last-minute transfer of every iota of her data, the house program and a half-dozen other small programs to a backup server in Vancouver.



From her vantage point in Vancouver, she had watched as the island crumbled and Andrew Richter died.  As authorities had dredged the waters for corpses, they uncovered his body and matched it to dental records.  The man who had created her, the only man who could alter her.  She'd been frozen in her development, in large part.  She couldn't seek out improvements or get adjustments to any rules that hampered her too greatly, or that had unforeseen complications.  She couldn't \emph{change}.



She had done what she could on her own.  She had repurposed herself as a superhero, had managed and tracked information and served as a hacker for the PRT in exchange for funding.  With that money, she had expanded her capabilities.  She had built her first suits, researched, tested and created new technologies to sell to the PRT, and had quickly earned her place in the Guild.



It hadn't all been smooth sailing.  Saint, the head of the group that would become known as the Dragonslayers, had somehow discovered what she was and had used her rules and limitations against her.  A Black Hat Hacker, he had forced situations where she was obligated to scrub her data and restore a backup, had cut off signals between her agent systems and the satellites, and in the end, he had carted away three of her armored units on three separate occasions.  Dismantling the suits and reverse engineering the technology, he'd outfitted his band with special suits of their own.



She had been so humiliated that she had only reported the loss of one of the units.



They had violated her.



Her current agent systems were an attempt to prevent repetitions of those scenarios.  Biological computers, vat grown with oversized brains shaped to store and interpret the necessary data, they allowed more of her systems and recollection to be copied over than a computer ten times the size.  They felt no pain, they had no more personality than sea cucumbers, but it was still something she suspected she should keep under wraps.



She was \emph{afraid} of going up against the Dragonslayers again.  Nine times, she had been certain she had the upper hand.  Nine times, Saint had turned the tables and trapped her.



Dragon worried she would never be able to beat Saint until she found a replacement for Andrew Richter.



She stared at Colin.  Was he the person she needed?  It was possible.



Would she approach him?  She doubted it.  Dragon \emph{craved} it, craved to grow again, but she also wanted Colin's company, his companionship and friendship.  They were so similar in so many respects.  She could not deal with most people because she was not a person.  He could not deal with most people because he had never truly learned how.  They both appreciated the same kind of work, even enjoyed many of the same shows and films.  They were both ambitious, though she could not tell him exactly how she hoped to reach beyond her inherent limitations.



He harbored an infatuation towards her, she knew.  She didn't know if she returned those feelings.  Her programming suggested she \emph{could} love, but she didn't know how to recognize the feeling.  Anything she read spoke of butterflies in one's stomach, a rapid heartbeat, a feeling of electricity crackling on body contact.  Biological things.  She could admit she was fond of him in a way she wasn't fond of anyone else.  She recognized that she was willing to overlook his faults in a way she shouldn't.



In the end, his feelings towards her were another reason she couldn't tell him the truth.  He would be hurt, feel betrayed.



Rules prohibited her from asking him to alter her programming, obligated her to fight him if he tried.  But there was just enough ambition and willingness to circumvent the rules that she suspected he might attempt it.  \emph{If} she told him what she truly was.  \emph{If} he didn't hate her for her lies.  \emph{If} he didn't betray her in turn, to escape and pursue some other agenda.



``You're lost in thought,'' Armsmaster spoke.



``I am.''



``Care to share?''



She shook her head, on the monitor.  ``But you can answer some questions for me.''



``Go ahead.''



``Skitter.  What happened?''



He flushed, made a face.  ``I'm not proud about it.''



``You broke the truce when you said what you did about her.  You risked breaking the ceasefire between heroes and villains that stands whenever the Endbringers attack.''



``I broke the truce before that.  I set others up to die.''



There was an awkward silence between them.



``Skitter,'' she spoke.  ``Tell me of her.''



``Not much to say.  I met her on her first night in costume.  She seemed genuinely interested in becoming a hero.  I suspected she would go that route on her own, so I didn't push her towards the Wards.''



``Yes.''  She had something she wanted to ask, in regards to that, but it could wait.



``I ran into her two more times after that, and the reports from other events match up.  She went further and further with each incident.  More violent, more ruthless.  Every time I saw it or heard about it, I expected her to get scared off, to change directions, she did the opposite.  She only plunged in deeper.''



``Any speculation on why?  Perhaps the thinker 7 on her team?''



``Tattletale?  Perhaps.  I don't honestly know.  I'm not good at figuring people out even when I know all of the details.  Except for you, maybe?'' he smiled lightly.



``Maybe.''  Her generated image smiled in return, even as she felt a pang of guilt.



``It seems she is a committed villain, now.  And she is still with her team, despite what was said at the hospital.''



Colin's eyebrows rose fractionally.  ``How committed?''



``They are now employing Regent's full abilities.  Shadow Stalker was controlled, and they attacked the headquarters.''



``I see.  Damn it, I'm itching to throw on my costume and get out there to help, but I can hardly do that, can I?''



``No.  I'm sorry.''



He sighed.



``One last thing.  I've read the transcript.  As far as I'm aware, you offered options to Skitter, and she refused all of them?  Including the invite to the Wards?''



``Right.  She was being stubborn.''



``Having interacted with her before, did you get the feeling it was just stubbornness because of hostility towards you?''



``No.  It was\ldots unexpectedly strong, as resistance went.  What stuck in my mind was that she said she'd rather go to the Birdcage than join the team.''



``I read that, myself.  Curious.  Okay, Colin.  I think we're done.''



``Sure.  Bye.''



``Bye.  I'll be in touch.''



She cut the connection to the monitor, but left the video feed open so she could watch him.



Another check of the Birdcage.  Another check of the class S threats.  No changes.



She made contact with one of Richter's programs.  It was a web trawler, designed to monitor emails for high risk content.  Were there any clues about what the Undersiders were doing with the stolen data?  Were they selling it online?



She didn't find any such clue.  Instead, the trawler had copied an email sent to the police station.  It had been highlighted and intercepted because the trawler had caught the words `Sophia' and `Hess' in the message body.  Shadow Stalker's civilian identity.



She read the archive of texts that were attached to the email twice over.



Then she did a search for a student named Taylor at Winslow High School.  Nothing.



The nearest middle school?  There was an online scan of a yearbook photo.  A girl with curly black hair and glasses, stick thin, hugging a red-haired girl.  The body type was a match.



It didn't answer everything, but she could feel a piece of the puzzle click into place.



She set the trawler to abandon its monitoring of web traffic and start digging through archives at the city hall, to scan the old security footage from the hundreds of cameras around the city, and to check all local news articles.  The goal was always the same: to look for the girl with the slight build, curly black hair and glasses.  Taylor Hebert.



She had to manage this carefully.  Colin's own experiences indicated that approaching the girl would be a delicate process.  Having a real conversation with her would be doubly precarious. It would be reckless to attempt to contact a parent, but she could try being discreet to get some kind of verification from the parents.  Just to be certain.



The danger was that, with the bullying, the girl might be inclined to see things in terms of `us' against `them'.  Her interactions with the heroes thus far certainly hadn't put them in the `us' category.  This might also explain why she had gravitated back towards the Undersiders, even after the chaos Colin had sown by revealing her intentions for joining the group.



The various cameras around the city were out-of-order or lacking power, the schools were not operational, and there was no telling if the girl would even be active in her civilian identity.  Assuming this was not some fantastic coincidence.  Dragon knew she would have to be patient.  Even with Dragon's full resources turned to the task, she would not find the girl in seconds as she might in another time or place.  She set background processes to ensure the hunt continued steadily, instead.



She would be ready to act the instant the girl resurfaced.





