





``I'm letting you go,'' Regent lied.



He made Shadow Stalker drop to all fours on the ground and forced a grunt from her mouth.  With the same ease as he moved his own body, he made her load her bolt and spin to point her crossbow at him.  There was no danger of her shooting him; he was fully in control from start to finish.



He could feel her striving and straining to move her finger, to pull the trigger and plant an arrow just above his collarbone.  Every iota of her willpower must have been focused on the task.



``There's a catch,'' he spoke. ``My power?  Once I've figured someone out?  It's a \emph{lot} easier to control them, after.  Any time you come near me, I can do this.  I can use my power and retake control in the blink of an eye.''



He had her raise her crossbow and point it at her temple.



``Next time I get control?  I'm keeping you for a full day.  Maybe two, if I feel like pulling an all-nighter.  And here's the funny part,'' there was no humor in his voice, ``I'm going to do it even if I'm in civilian clothes, if my power tells me you're in range.  You won't even know when it's coming.  You're now a liability to the Wards, and you won't ever know when or where I'm going to get control again\ldots''



``Unless you leave.  Skip town.  Join another team.''



He had her nod, stiffly, awkwardly.  He felt her rising heartbeat, the slight increase in her breathing, which he managed, controlled.  Her muscles clenched, an involuntary reaction just beyond the scope of his control.  She'd realized what he was doing.  Rather, she knew what he \emph{wasn't} doing.



He wasn't letting her go.



``Now let's walk you off to the other end of the city before I release you.  I don't think you're quite stupid enough to try and follow us, but I think my teammates would be more comfortable if they were sure.''  He rolled his eyes.



That said, he turned her around, activated her power and walked her through the door.



Regent looked at the others, shrugged.  ``Good enough?''



Using the shadow form, she could cover a lot of ground very quickly.  For long minutes, he exercised her power, the ability to be as light as a feather, enjoyed it.  He even liked the running, too, when he turned off her power and just legged it.  This girl was in good shape.  He could tell she exercised regularly, that she ran on a regular basis.  Running was almost effortless, and it felt \emph{good,} even with the aches and pains of the recent brawl. Months or years of practice had fine tuned her body.



Fighting had been much the same way, but it had been even better.  Her muscle memory had been so primed for punching, kicking, takedowns and evading that he'd almost been able to let her go on autopilot, let her body handle things on its own.



Not that he could, really.  But it had been \emph{easy}.  He loved that sort of thing.  Maximum reward for minimum effort.



That same philosophy of minimizing the work he had to put in, sticking to what he enjoyed and the things that interested him, it was an advantage here.  Brian, Lisa and Taylor had their own dynamic.  They were friends.  He considered Brian a friend, but it was more along the lines of someone he could play video games with, talk about movies.  It wasn't much different from if they were coworkers or roommates.  He smiled at the thought.  They kind of were, when it came down to it.



Regent knew he was a background character, for the most part.  He played along, he didn't make waves, he didn't stand out.  He wasn't close to any of the others.



He was cool with that.  In fact, it suited him perfectly.



He was cool with it because it meant that when they were all heading out to meet Coil, nobody noticed that he was distracted, or that he wasn't joining in the conversation.  His control got worse as the distance between himself and his puppets widened, which meant he had to devote more focus to Shadow Stalker and the act of keeping her movements fluid.  He ran into the same issues when he controlled more people, and there was the irritating side effect that his own coordination, speech and fluidity of movement all suffered to the same extent that his `puppets' did.  Were he to open his own mouth now and speak to Brian or Taylor, he might stutter or slur his words.  It was almost more trouble than it was worth.



Almost.  He was surprised to realize how much he'd missed this.  It was like a high, a whole other set of emotions, of physical sensations.  Real life, just being Alec, only Alec?  It paled in comparison.  It was \emph{dull}.



He wondered sometimes if dealing with his father had messed up something inside him.



He could remember being young, maybe eight or so, fighting with two of his sisters over the fact that he'd wanted to watch the music channel and they wanted to watch some craptastic stop motion cartoon.  They'd outnumbered him two to one, and he'd known he would lose the argument.  So he'd thrown a tantrum, started screaming.



The entire atmosphere in the house had changed in a second.  His sisters went from argumentative to conciliatory in an instant, changed the channel to the music, tried to give him the remote.  One of father's `girls' came in and tried to quiet him down.  When he hadn't, she'd clamped a hand over his mouth.



It hadn't been enough.  Dear Old Dad had come marching out of the master bedroom.  Nikos Vasil.  \emph{Heartbreaker}.  Tall, wearing only boxer briefs, with a muscled, lanky physique, long hair plastered to his head with sweat.  Father had taken two or three seconds to assess the situation before using his power on Alec, his two sisters and the `girl' with a hand over Alec's mouth.  He hit each of them with stark terror.  The kind of fear you experienced when you were claustrophobic and you woke up in a coffin six feet underground.



Then father had gone back into the bedroom and slammed the door behind him.



It had been around summer when that happened, Alec mused.  He didn't have many ways to tell time, back then, since he hadn't gone to school, and the days kind of passed.  Still, it had been hot, he remembered.  Between that summer and Christmas, Alec hadn't opened his mouth to speak once.



That was only one of a dozen or so experiences that came to mind.  So yeah, maybe father had broken something in the process.  Maybe it had been the emotional equivalent of staring into the sun for far too long, too many times, being left almost half blind.



Or maybe it was his own power.  He could be two, three or four people at the same time, feeling what they felt.  By the time he was a teenager, he'd experienced every kind of drug, in someone else's body, had slept with himself as various boys and girls.  How was being just ordinary Alec supposed to compare?



\emph{Shadow Stalker} wasn't emotionally dulled.  Her emotions were rich, uninhibited.  She was  passionate in her emotions: angry, judgmental.  Even the negative feelings were something he could savor in their own way.  He wasn't really experiencing them – it was more of a very involved spectator role.  Her fear was thrilling in the same way a fantastic scary movie was, with the detail and the immersion cranked up to eleven.



He leaped straight up into the air, then activated the shadow state.  When she was as high as she would get, he had her grip her cloak in her hands and use it to guide her descent so she could land atop the roof of the gas station.  He stopped, stretched her arms.  She was breathing hard, but not as much as his Alec-self would be after even half as much running.  He could feel the endorphins being pumped into her body from the hard exercise, and he was all the more aware of it because he had his other body to compare to.  She was an athlete.



He ran her hands down her chest, felt her breasts, the muscles of her stomach.  Stretching once more, he clenched her hands, felt the muscles in her arms flex.  He felt her shudder in revulsion.



``Almost forgot you were in there,'' he murmured, barely loud enough for her to catch.  Not that it mattered.  She was as aware of the movements of her mouth as he was.  He could mouth the words and she would probably understand.  He smirked for her benefit as much as his own.



``So.  Bet you're wondering what's up,'' he commented.  ``Funny thing about having this control over you, I can feel your emotions, your body's reactions.  Like a really, really good polygraph test.  I wasn't even half done saying my piece back there when I caught on to the fact that you were too pissed and too angry to back down and walk away.  There's no way you're going to leave town if I let you go, right?''



He felt her struggle to open her mouth and respond.  He could have let her, by giving her some limited control over her own movements, but he didn't.



``Right.  So I'm taking it upon myself to ensure this all goes smoothly.  My teammates have other shit to worry about, and I'm kind of enjoying flexing my powers.  So I'm dealing with this situation myself.  You and I?  We're going to go another route.''



He fished in her belt and pockets and began withdrawing the contents.  He tossed the things he couldn't use over the edge of the roof.  Billfold, spare cartridges for the crossbow, a small knife, spare strings for the crossbows, bandages, keys and a Wards ID card fell to the ground by the side of the gas station, in and near an overflowing dumpster.  There were plastic cuffs in the belt, but he couldn't be bothered to fish out every last one and throw them all away.  At the right hip, he found two cell phones.  Success.



One of the phones looked years out of date.  The screen was scuffed so badly it was barely readable, and the plastic cover for the plug slot at the bottom was missing.  The other was a touch screen smart phone.  He didn't recognize the make or the model, and the interface when he turned it on and touched the screen was unfamiliar.  Special issue from the Wards?  Whatever.  Not important.



The smart phone was password protected.  That was more Lisa's thing, but he did have one trick up his sleeve.  Holding her fingers above the keypad, he let them follow through with the most natural feeling sequence of numbers, ingrained into the mind-body connection through the habitual repetition of a sequence of movements over weeks or months.  Muscle memory.



It took two tries.  The first felt slightly off at the end.  The second was spot on, and was rewarded with a vibration of the phone and a menu.



``Contacts,'' he murmured, pressing a button, ``Weld, Clockblocker, Vista, Flechette, Kid Win\ldots boring.  Nothing I can work with, here.''  Director Piggot?  No.  Some potential there, maybe, but she was probably on top of this body-snatching situation.  Fully informed.



He scrolled down.  Beyond the contacts that had been pinned to the top of the list, there was a short list of contacts that were sorted in order of who had been contacted most recently.  At the top of the list was an `Emma Barnes'.



He checked the other, older phone.  No password.  A quick examination showed it was her civilian phone.



``Taking this out on patrol?  Is that stupidity or arrogance?  What if you lost it?''  He shook his head, then offered her a dramatic gasp, ``What if it got into the \emph{wrong} hands?''  Her voice was far better for the gasp than his own was.  He couldn't help but chuckle after hearing it.



This Emma girl was listed in both of the phones.  Now he had a strong suspicion as to who it was.  A quick read of the received texts gave away Shadow Stalker's name, but he already knew that.  Taylor had let it slip, before.



Her pulse was pounding now, and he could feel a growing sense of\ldots what was that?  Outrage?  She was pissed at the invasion of privacy.



He tried a giggle on for size, to see if he could, and to see if it irritated her.  It worked on both counts.



No text messages had been exchanged on the smart phone, so he dug through the archive of old texts on the crummy old phone.  Lots sent to Emma.  Some sent to a Madison.  Others, relatively few, to a mom, a Terry and an Alan.



When he'd gotten sick of paging through the texts in the order that they'd been sent, he went looking for the saved texts, the messages Sophia had deemed important or noteworthy enough to save from being deleted.  What he uncovered was telling.  He had to do more digging to find the rest of the discussions for each message Sophia had saved, in order to get as much a sense of things as he could.  It was hard, when each series of texts was in response to some event he hadn't participated in.



Some were inane, others he just didn't understand.  Then he found one that gave him pause, that confirmed his suspicions about who Emma was.


\msgbox{Emma: what r u doing with her bag?}

\msgbox{Sophia:  am in art class atm.  was thinking i can fill it with paint when teach leaves room.  put it in lost\&found.  her art midterm is inside so she might look for it and find it and}

\msgbox{Sophia: be all yay i found it and then she looks inside and sees its fucked}

\msgbox{Emma: lol.}

\msgbox{Sophia: what did you say to make her cry?  that was awesome.  blew my mind.}

\msgbox{Emma: (SAVED MESSAGE) crying hrself to sleep for a week?  she told me she did after her mommy died}

\msgbox{Sophia:  you r so evil}

\msgbox{Emma: ya ya}

\msgbox{Sophia: can i use that one on her?  saving that one for posterity btw}

\msgbox{Emma: won't have same bite to it.  brilliant bit was the suprise.  that slow realization abt what i meant.}

\msgbox{Sophia: teach me o master}

\msgbox{Emma: lol}

\msgbox{Emma: wont be as good but i was thinking of that day.  think i remember musc we were listening to when she got the phone call abt her mom.}

\msgbox{Emma: we shld wait a while and then see if she cries agn if we play it in hallways or b4 class.}

\msgbox{Sophia:  and we cant get in trouble for just listening to music}

\msgbox{Emma: ya}

\msgbox{Sophia: cant believe you were her friend.}

\msgbox{Emma: she was lame but not depressing and lame @ same time.}



Regent closed the phone, threw it casually into the air, and then caught it on the way down.  He did that a few more times, thinking.



``Huh,'' he said.



Long seconds passed.  He knew he \emph{should} feel bad for the dork, but he only felt annoyed.  He felt worse about the fact that he \emph{didn't} feel bad than he did about what he'd just read.



Something to thank father for, maybe.



``You are not a nice person,'' he spoke to Sophia with a note of irony in his voice.  He could feel her try to respond.



He smiled slowly, ``Let's see\ldots''



He thumbed through the phone's menus until he found an email option.  He verified it could send attachments.



The smart phone in his other hand, he found the web browser and did a search for local high schools.



``Hmmm.  What school do you go to?  Arcadia?  No.  Immaculata?  No.  Clarendon?  Nope.  Winslow?''



He felt the slightest of reactions from her.  A hitching of breath, maybe.  And there was nothing she could do to stop it, because the reactions were hers only because they were \emph{involuntary}.



``Awesome.''  He searched for the web site for Winslow High School, and whistled tunelessly to annoy Shadow Stalker as he found the teacher's emails.  He began painstakingly entering them into the recipient field.



When he'd done that, he began the process of attaching the texts to the email.  It would have been mind-numbingly dull if it wasn't for that gradually building sense of trepidation he was experiencing from his gracious host.



He typed out a message for the email itself:


\msgbox{found phone.  stuff inside is concerning.  thought u should see what ur students r doing.}



Her thumb hovered over the button that would send the email.



``Nah,'' he decided.  He felt a wave of relief from his host.



That relief swiftly faded as he turned her eyes to the smart phone and searched for Brockton Bay's police force.



When he'd added \emph{that} email to the list, he added another line:



\msgbox{contacting police to make sure something is done}


He sent the email.



He felt an explosion of rage from within Shadow Stalker's body.  Her hands even shook with it.  He laughed, and her anger mixed with his amusement to create something that sounded unhinged.



Probably was, when he thought about it.  She had multiple personalities, in a way.



He stepped from the roof, and waited until the last second to use her power.  Her body exploded into a cloud of shadows.  As she pulled back together, he felt a strong discomfort.  Not quite pain.  In seconds, she had condensed back to her normal form.  The pain his hosts felt was something distant.  It didn't bother him half as much. He couldn't be sure if it was because he instinctually prevented it or if it was something else.



He resumed his whistling as he hopped up onto the railing of a bridge and walked atop it.  He dialed Emma, felt a mild reaction from his host: Annoyance with a note of anxiety.



Emma picked up on the fourth ring.  ``What the fuck soph\ldots what the fuck!?  It's three AM!''



``Terribly sorry,'' Regent tried to sound convincing, but it came out sounding sarcastic.



``You said you'd call me hours ago, to give me a recap.''



``I'm sorry,'' Regent didn't trust himself to pull off a sincere apology, so he lowered her voice to a hush instead.



``What's going on?''



``I needed to talk to someone,'' he spoke.



``\ldots{}Are you hurt?  What happened?''



``Nothing.  There was this brawl at the headquarters, Dragon showed up, but that isn't what I wanted to talk about.''



Regent held his breath, waited.



``Seriously, you've got me worried.  You're making it sound like this important thing, and you woke me up at ten past three in the morning, so it had \emph{better} be important.  Dish.  Explain.''



``I'm lonely.''



Emma's voice rose in pitch, irritated, ``\emph{Seriously? That's} your issue!?''



``I miss you.''  He knew she wasn't in town from the most recent texts he'd read on the phone.



``This doesn't sound like you.  Are you high, or did you get poisoned or something?''



``I \emph{really} miss you,'' Regent breathed into the phone.



``What.''



``I've been in love with you from the beginning.''



``Sophia, stop.  If this is a prank--''



``Why do you think I pushed you to turn on that depressing little shit of a friend, way back then?  I was \emph{jealous} of her.''



``This is retarded.  Don't fucking call me again until you're ready to grow up,'' Emma growled.



``Please,'' Regent managed to pull off a pleading tone, but Emma was already hanging up.  He heard the dial tone and swore, ``Fuck.''



He hopped down from the railing as he reached the end of the bridge.  He commented,  ``Don't think she bought it.''



Sophia tried to respond, and for the first time, she almost succeeded.  The distance between Alec and Shadow Stalker was too wide, now.  It would only get worse.  He could feel it in his other body, too.



``Let's see,'' he grinned, raising the smart phone.  Her hand shook as she held it.  ``Ooh, maps.''



The map application still showed the last route Shadow Stalker had requested from it, detailing directions from a point in the south end of the Docks to a place downtown.



``Thirty-three Stonemast avenue.''



Again, that slight reaction from her that told him he'd found something.



``That got your attention.  Let's go pay a visit.''



He set the phone to display directions from their current location to Stonemast avenue, and then he ran once more.



Her movements were more awkward, now.  Her reflexes were slower, her balance worse.  Activating her power was becoming a chore, a slower, harder process.  Above all, it required more of his attention.  He had his Regent-self put his headphones in and turn on some music.  It was an excuse to ignore the others, and to have his attention elsewhere.  They weren't at their destination yet.



Shadow Stalker reached Stonemast avenue before Regent, Tattletale, Skitter, Imp and Grue got to Coil.  It was funny, but with the route they were taking, if the timing was a little different, the group could have theoretically crossed paths with Shadow Stalker.  At least his control was improving as the gap between them closed.



Thirty-five, thirty-four, thirty-three.  It was a residential area.  The houses here weren't in the best shape, and a lot of houses had trash or belongings in the yard.  Thirty-three Stonemast avenue had a toddler's toys sitting on the front lawn.  The hedges between the property and the neighbors was overgrown, and the tree at the front of the property looked dead.  It might have seemed deserted, but someone had taken up the effort of picking up the detritus the tidal wave had brought in and piling it at the front corner of the lawn, by the driveway.



He walked her through the front door, felt rising anger and worry from his host.



That anger and worry peaked when a young man, nineteen or twenty, stepped from the living room to the front hall, heading towards the kitchen, and saw her.  The man stopped and stared.



``Mom!''  He shouted.



A tired looking middle-aged woman entered from the kitchen, holding a four-year old girl in her arms.  Regent had grown up around lots of kids.  He liked to think he was a good judge of ages.



The woman stared at Shadow Stalker, then turned, ``Terry, take your sister upstairs.''



``But--''



``Now!'' the woman barked.



Terry moved to pick up the child, who was looking increasingly concerned over the raised emotions and the strange person in their hallway.  Regent reached out and grabbed Terry's arm.



``Chill, bro,''  Regent was making a guess here.  From the way the boy stared at Shadow Stalker, he knew he'd hit the mark.



``\emph{Sophia!?}''



``Yeah,'' Regent grinned behind her mask.  ``Duh, moron.''



The woman stepped between Shadow Stalker and Terry, a look of fury on her face, ``Sophia!  Kitchen.  Now!''



With a swagger, Regent walked Shadow Stalker into the kitchen.  There was a flurry of hissed words between Terry and Shadow Stalker's mother.  Among them was a surprised, hurt, ``You knew!?''



Regent sat down at the kitchen table and put her feet up.  Dirty water pooled on the table's surface.



It was nearly a minute before the mother came storming into the kitchen.  She pushed Shadow Stalker's feet off the table.



``Explain!'' she demanded.



``What?'' Regent lifted one shoulder in a shrug.



``We had a deal.  You could do this thing of yours, but your siblings were \emph{not} to know!''



``It's a pain in the ass,'' Regent said.  He pulled off Shadow Stalker's mask and started tapping the edge against the table, idly.



``It's the rules in \emph{my} house!  If it's going to keep you out of prison and on the straight and narrow, \emph{fine}.  But I will not have you glorifying violence--''



The mother stopped mid-sentence as Regent opened Shadow Stalker's mouth in a very real yawn.  Funny that his other self yawned as well, in that sympathetic reaction to someone else yawning.  The mother slapped the mask from Sophia's hand.  It clattered to the ground.  ``Listen to me!''



``Whatever,'' Regent drew a crossbow and turned it over in his hands.



The mother stared at it.  Her voice was hushed as she spoke, ``That doesn't look like the tranquilizer dart the Director showed me.''



Regent quirked an eyebrow, ``Oops.''



``What are you doing, Sophia?  Do you \emph{want} to go to jail?''



``I'm bored,'' Regent replied.



``You do \emph{not} have the right to complain about something like being bored!  I work two jobs for you three!  I put in overtime, I attend every school function, I come into the office every time you get reprimanded because you've got anger issues!  You aren't even taking care of your sister, or helping out around this house!  What do you think--''



``And now you're making me even more bored,'' Regent cut her off.



The mother slapped Sophia so hard that her head turned to one side.  Her cheek burned.



``Don't you \emph{dare},'' the mother intoned.



Shadow Stalker stood at Regent's directions, then pointed the crossbow at the mother.  The woman's eyes widened, and she hurried to back away as Shadow Stalker advanced.  They stopped when the mother's back was to the wall by the kitchen door, with Shadow Stalker's crossbow bolt pressed against her throat.



``I think I'm done with listening to you whinge,'' Regent whispered.



``What are you doing?  What's \emph{wrong} with you?''



``Like you said,'' Regent shrugged, ``Anger problems.  I promise you, you don't have the slightest idea of what I go through.''



When in doubt, be vague.



``If you're talking about Steven\ldots''



Steven.  Regent could feel a reaction from Shadow Stalker at the name.  ``I'm not talking about \emph{Steven}.''  He put some inflection in the name.  He dropped the crossbow to one side, stepped away and stretched.  The mother didn't budge from where she was pressed up against the wall.  ``I'm going to my room.  Don't disturb me.''



He bent down and grabbed the mask, but he didn't put it back on.  He stepped out into the hallway, and saw a vacuum cleaner parked in the corner.  An extension cord trailed from it to a neighboring room.  An office?  He unplugged the cord from the wall and the vacuum, and then headed upstairs, winding the cord into a simple coil.



Shadow Stalker's body was a cocktail of emotion.  Fear, anger, anxiety, worry, panic and sheer fury.  Regent staved off the worst of the physical reactions, the trembling and the heavy breathing, and managed to make Shadow Stalker seem calm as she reached the top of the stairs.  Terry was up there in the hallway, staring, uncomprehending.



Regent found her room, then shut the door.  It was small, old-fashioned, with wood paneling on the walls.  The furniture was limited to a twin-sized bed, a vanity with a mirror, candles and cosmetics littering the top, a bookshelf and a combination computer desk and dresser with a computer and a printer perched on top.  The wall behind the pictures showed Shadow Stalker with a redheaded girl.  There were a lot of photos with them laughing.  Emma?



``Emma?'' he asked.  That slight alteration in her heartbeat and her breathing told him he was right.



He found a picture of Shadow Stalker – Sophia – with her family.  Her mom looked younger and far less tired there, and was pregnant.  Shadow Stalker looked twelve or so, and her brother looked sixteen or seventeen, sporting a fantastic looking afro and a less fantastic attempt at a moustache.  They were clustered around one another, but only the mom was smiling.



Regent's eyes fell on the man who was cut out of the photo, only his hand on the mom's shoulder, and a sliver of his torso and leg were visible at the edge of the picture.



``Steven?'' he asked.  Raw hatred boiled up inside Shadow Stalker, for both Regent and the man that couldn't be seen in the picture.  ``Steven.  So what did he do do you?  Believe me, I've seen it all.  Hit you?  Touch you?''



No reaction from either of those.  Verbal abuse?  Emotional?  Something else?  He didn't care enough to quiz her more.



He grabbed the lighter from beside the scented candles and began pulling the photos off of the wall.  Using the lighter, he burned a hole in the photograph where Emma's face was.



``Well,'' he said, his tone dry.  He had to cough to keep himself from letting her anger turn his voice into a growl.  ``You sure rose above that shit, treating your classmates like you do, getting in fights, not helping out dear old mom.''



Again, he had to struggle to maintain control as she exploded with emotion.  It didn't help that his other self was trying to listen to what Coil was saying.  Better to avoid testing her.



``You and I are more alike than you'd suspect, I think,'' he said. ``We're both arrogant assholes, yeah?  Difference is, I admit it, I don't dress it up and tell myself that I'm a bitch and that that's a good thing.''  He burned Emma's face out of another photo.



``So, let's tie all this shit together.  I \emph{have} been working with a goal in mind, believe me.''



He got a piece of paper out of the printer, then found a pen in one of the drawers.  He was careful to rely on her muscle memory when it came to the handwriting.



I thought I could manage.



I'm too angry.  Too lonely.  I hate myself for what I'm doing.  Hurting people.



I hurt my mom.  I hurt my classmates as Sophia.  I hurt people as Shadow Stalker, and I hate myself for enjoying it.



I thought I could manage it.  I had Emma.  She had my back.



Except she turned me down.  I loved her, really loved her, and when I confessed she turned me away.  Acted like it was a joke.



This is the right thing to do.  I won't be able to hurt anyone anymore.



Terror surged through her body like ice water.  When he laughed in reaction, it came out shaky.  He littered the burned photographs around the piece of paper, with Emma's face missing from each, then drew an arrow from the crossbow's cartridge and laid it across the bottom edge of the paper.  It was overdramatic enough to work.



He stood on the chair and began wrapping the extension cord around the base of the light fixture.  He grabbed the cord and hung off it for a few seconds to verify it could hold her weight.  The light fixture itself was flimsy , but the frame it was attached to was bolted securely into the wooden beams of the ceiling.



He found moisturizers and soaps on top of the vanity.  Using them, he rubbed the end of the extension cord, making it slick.  Holding the end, he began tying it into a crude hangman's knot.  When he failed to do it right, he used the smart phone to find a video of how to tie one, then turned the volume all the way down.



``Here's the thousand dollar question,'' he mused, as he began following the steps outlined in the video, putting the knot together, ``Will your boss tell your mom what happened with me controlling you?  If she keeps her mouth shut, well, this paints a pretty ugly picture, doesn't it?''



A tear rolled down his cheek.  He scoffed a little, blinked the tears out of her eyes.



``But if she \emph{does} tell, if she lets mommy know, then shit hits the fan.  It looks pretty fucking bad for her, and if word gets out, it's as bad as it gets for public relations.  Scary, dangerous parahumans.  Not just lives at risk, but you could be controlled.  Ooooh, scary.  Nobody would ever be able to trust their coworkers or neighbors.  It's the kind of stuff they want to keep quiet.''



``Looks bad for me, sure, but you saw the fight earlier.  It's not like you guys are \emph{that} big a threat.  Like I said, I'm arrogant that way.''



He reached to plug the extension cord into the wall, but found it too short.  He sighed and went to unplug everything from the computer's power bar and use that to extend the length of the cord so he could plug it in.  He grabbed her alarm clock, stood on the chair, and plugged it into the noose.  He put her hood down, and then set the alarm clock inside her hood, blinking 12:00, 12:00, 12:00.



``Any last words?''  He slid the noose around her neck.  It was slimy with the soaps and other shit he'd poured on it.



He gave her enough control to speak, but retained control of her arms, legs so she couldn't escape, and held her diaphragm so she couldn't draw in enough air to scream for help.



``Why?'' she breathed.



``You fucked with my teammate,'' he shrugged her shoulder.



``Grue?  I--''



He didn't let her finish.  ``I dunno if I care all that much, but it's the sort of thing I'll do because it feels like I should.  Dunno.  There's also the fact that you're dangerous, and you've outlived your usefulness, so\ldots unless you can give me a convincing reason.''



``Please.''



``Not that convincing.''  He raised one foot, then kicked the chair, hard.



It rocked, but didn't tip over.



He chuckled lightly, feeling the confusion and the relief from his host.  It was a thrill unlike any other.  ``I think I made my point.''



She wanted to respond, but he didn't let her.  She was bewildered, just as scared as she had been before.



``I'd like to think that you have much less reason to hang around this city than you did an hour ago.  Even if she hears how you were controlled by yours truly, mom's not going to be so comfortable having you around in the future, given the dim possibility of a repeat performance.  Things are going to be awkward with Emma there, too.  Your career as a hero here isn't looking good, either.  Eff why eye, I \emph{was} telling the truth about my ability to assume total control faster, easier, if I've controlled someone before.''



He fished out a set of the plastic cuffs and put them around her wrists, then worked her fingers to pull the end and cinch the cuffs tight, behind her back.



``I can feel your emotions.  I \emph{know} I've convinced you.  You leave town, and if you don't want me paying a visit, wherever you wind up, you keep your mouth closed about tonight.  They don't need to know this was all my doing.  Things get messy that way, yeah?''



He gave her limited control, and she nodded, fractionally, as if afraid to move.



``If I do get control again?  I won't pull my punches.  Or my kicks.''  He tapped her foot against the back of the chair.  Her heart leaped in her chest.  ``You can't feel \emph{my }emotions, so you'll have to trust that I'm capable of it.  You know I'm Heartbreaker's kid.  You know I've killed before.''



Again, she offered a slight nod.  She tried to speak, but he didn't let her.  No need, he could guess, from what she was feeling.  The anger was gone now.  There was only fear.



He glanced out the window.  There were flashing lights.  A PRT van?  Or maybe a police car.



A chuckle escaped her lips.  ``Well, I'll leave it to you to get out of this situation.  When you do?  Get the fuck out of my city.''



He let out a breath, and then relinquished control of her body back to its owner.

