





One of Rachel's dogs growled, long and loud, an alien, unsure sound.



She shushed it, setting her hand on the side of its head.



``Ugh,'' Cozen mumbled, ``The smell.''



The smell.  Summer heat, the mingled scent of blood, shit and overripe bodies, with traces of other things in the wind.  Caustic chemicals, ozone, smoke, burned flesh and plastic.



It wasn't unfamiliar.  Not an exact combination of smells I'd smelled before, but it put me in mind of Brockton Bay in the days soon after Leviathan had attacked.



I looked up at the man who'd been strung up overhead, spread-eagled.  Chains stretched from his wrists to buildings on opposite sides of the street, and more chains extended from his ankles to the bases of the same buildings.  A number was carved on his chest.  \emph{One-seventeen}.



Beneath him, the sign from outside the town limits had been slammed down onto the hoods of two cars so it stood upright.



\emph{Welcome to Killington.  Heart of the Green Mountains}.



They probably thought it was funny.  Especially with the bloody handprint on the word `heart'.



``They got the children too,'' Cozen whispered, as she averted her eyes from a mother who had died holding her child, both burned black.  The only parts of their body that hadn't burned were patches of skin in the shapes of numbers.  \emph{Two-fifty-four.  Two-fifty-five}.



Two of the Red Hands, Getaway and Rifle, had come along for the ride.  They were sticking close by her, and formed a small contingent with Grue as a consequence.  Getaway wore a cowl with a hood that peaked in the front, to the center of his mask.  His costume had straight, clean lines, as though he'd modeled it after a car.



Rifle, by contrast, didn't look like he wore a costume.  He was dressed like a special ops agent, complete with a complicated night-vision mount around his eyes, a number of scopes with lenses glowing in hues ranging from blue to red.  Violet scopes were currently fixed over his real eyes.  He carried a weapon, a modified gun that wasn't, as far as I could figure it, an actual \emph{rifle}.  It looked like it was set to fire specialized loads from canisters.



\emph{Of course they got children, }I thought.  I had to bite back a retort.  Why was she here, if she wasn't ready for this?



But she wasn't a fighter.  None of the Red Hands were, really.  They were professional thieves.  Break in, get out, sell the goods.



They were, maybe, what the Undersiders might have been with a little more luck, slightly different personalities, and a quieter existence.



Without me, even.



The Undersiders had made it for a year and a few months with their original strategy, avoiding fights, slipping away, staying off the radar.  They would fight when they had to, but they didn't make it a thing.  The fact that they didn't have firepower meant they \emph{couldn't} make it a thing.  If anyone got into trouble, it was the dogs.



And then I joined.  Starting with the bank robbery, I pushed them to switch up tactics, catch the enemy off guard.



If I'd never joined, what would have happened?  Maybe the bank robbery wouldn't have worked out, and one of them would have been picked off and arrested.  Maybe they would have taken a different direction with the robbery.



Bakuda might have killed them, Coil might have pushed them to be more aggressive as he scaled up his plans.  Or they could have found a way, could have continued going the way they did, less violent in general.



Some good, some bad.  Rachel might never have reached the point she was at now.  Grue wouldn't necessarily have gone through what he did.  Regent might be alive.



I glanced again at Cozen, saw her looking at me in turn.  Catching me looking, really.



``What?'' she asked.



\emph{You don't need to be here.  You'll be happier in the long run if you aren't}.



``Nothing,'' I responded.  She looked annoyed, but she didn't say anything.



There was a kind of art to the setup.  No doubt at all that it was a display, a showpiece.  Trails of blood, ash and other substances marked where bodies had been moved.  They were spaced out just enough that we would run into a fresh one just as we left the last behind.



I might have missed it if not for my swarm-sense.  The bodies were placed at positions high and low, the methods of death differing here and there, but there was a pattern to their distribution.  The kind of pattern that might become clear if one were to set up a map and note the location of each body on it.  A spiral.



I pointed the way to the central point of the spiral.  I could see a plume of smoke in that general direction.  Not the middle of Killington.  Skewed off-center.



``\emph{Weaver, report},'' Revel's voice.



``I'm here,'' I responded.  I kept a finger at my ear to make it clear that I wasn't talking to myself.



``\emph{Killington?}''



``Yes.  Progress is slow.  I'm sweeping the area for traps and potential ambush, and I'm marking a path to travel for when the others get here.''



``\emph{We saw the two traps at the outset.  There are more confirmed?''}



``Yeah.  I'm not touching anything.  Pass on word that any capes entering the area should be hands off.  I activated one and it was only a decoy, a prelude to a gas attack.  One of Bonesaw's, I think.  Grue warded it off.  No casualties.''



``\emph{I'll make doubly sure to pass on word about the traps and about the route you've cleared.  I would have warned them anyways.  The initial casualties were enough, with the helicopter and first responders.  Give me a second.''}



I led the way as our group rounded a corner, and saw the smouldering wreckage of the helicopter, smoke still streaming skyward.



The collision apparently hadn't been enough to topple the corpse that stood upright in the middle of the intersection, desiccated.  A number was drawn on the mummy's chest in blood.  \emph{Number thirty-six}.



I could make out a tripwire strung between him and another corpse, a woman.  She had apparently been shot execution style, propped upright on her knees.  A number, again, had been drawn out in the midst of the blood spatter from the original wound.  \emph{Number two-sixty-five.}



The tripwire was almost obvious, coated in congealed blood.



\emph{Red string}, I thought.  In Japanese superstition, it was the string that bound lovers.



The pieces suggested Crimson and Winter.  Neither was Japanese, but the idea of mingling romantic imagery with violence in that way fit them.  The red knight and the soldier.



``\emph{I've got the feed open now},'' Revel said, ``\emph{Seeing what you're seeing.}''



``Only part of it.  The way the bodies are laid out, it's a spiral.  I think it all points to something.  Making our way in.''



``\emph{Technically you aren't.  You've stopped}.''



``Tripwires,'' I said.  ``Being very, very careful.''



``I like being careful,'' Imp commented.  She'd only be hearing one side of the conversation.  ``Careful is good.  Keeps us alive.''



``Being too careful gets you killed,'' Rachel commented.  Of everyone present, she seemed least concerned with the amount of death that surrounded us.  Then again, that didn't surprise me.  ``Have to act when you see the chance.''



``You want to hop on your dog's back and charge ahead?'' Imp asked.  ``Go activate every trap between here and wherever?''



Rachel frowned.  ``No.''



``I \emph{like} careful,'' Imp restated, for the record.  ``Let's be careful.''



``Yeah.  Fine.''



I pointed to indicate.  ``Obvious tripwire here.  Covered in blood.  Connects to the two bodies and\ldots I think claymores, at the base of that building over there.  There are other tripwires around it.  Look too hard at it, miss the others.  I think there's a pressure plate, too.  I'm not sure what to call that.''



``I don't see anything that could be a pressure plate,'' Grue observed.



I pointed at a pane of glass at the base of a pile of rubble.  It was broken, with a narrow thread of wood still attached along the one edge that was straight and unbroken.



``Maybe.  Kind of hard to believe,'' he said.



Because we could see through it?  Yeah.  But it was situated beside a pile of rubble, and the balance of the glass with the surrounding brick and concrete seemed too \emph{convenient}.



Was there something attached to the edge of the glass where we couldn't see?  If the glass was broken, would the wood weigh the remaining fragment down and pull something?



``Let's play it safe.  We avoid the tripwires, we avoid the glass.''



``Whatever you say.  I'm all for playing safe,'' he responded.



I led the way around the trap.  I left a trail of dead bugs behind us as we made our way to the center, murdering them with larger bugs and mashing them into the ground.  A path.



I wondered about Grue.  Couldn't read his expression, couldn't note his tone either.  Was he thinking about the same thing I was thinking?



We'd already fallen for one trap.  Not \emph{here}, but back in Brockton Bay.  Back \emph{then}, when he'd had his second trigger event.



It had been the Nine, back then, and though he wasn't giving me any clues there was something \emph{wrong}, he wasn't indicating that he was his old self, from back in the good old days.  I suspected he hadn't fully bounced back, even after all this time, might never.



We circled around eight teenage girls, sitting in a circle, crowns of splintered wood nailed through their skulls.  One had fallen over in response to the wind, but the others were still upright, propped up with wooden planks nailed into their spines.  Less blood than the head wounds, I noted.  Some pre-death, others post?



The numbers were on the pieces of wood, registration numbers or something from the crate that had been smashed for materials.  \emph{One, two, three, four, five, six, seven, nine.}



I looked up.  Number eight sat on the bulb of a street light, a long dress blowing in the wind, directly above the circle.  Her crown was the tallest, and for her to be so rigid, there had to be a whole assortment of planks nailed to her.



``Nine Kings,'' I said.



``A woman king?'' Imp asked.



``She's the victim,'' I said.  The killer is her\ldots husband, for lack of a better word.''



``\emph{They've resurrected all of the old members.  Cloned them,'' }Revel said.



\emph{Clones}, I mused, agreeing.  My suspicions were confirmed, and I wasn't surprised.  I'd hoped for different, but the reality of what we faced had been hinted at early on, when it had been revealed that the Nine had hit a tinker's laboratory and made off with materials that could be used to mass produce lifeforms.



King.  The leader, the founder of the group.  Were the numbers in an order corresponding to when they had joined, then?  Would the second member of the Nine be ten through eighteen?



``Got a live one!''  Imp called out, interrupting my thoughts.  ``\ldotsKind of alive.''



I turned to look.  A fat man was shifting in a restless way, his chest rising and falling quickly in unsteady movements.  One arm jerked.



``Leave him,'' I said.  ``Don't touch.''



``He could be a witness,'' Rifle said.



``Or a trap,'' I responded.  ``I doubt he's in a state to fill us in on anything.  We'll move on, wait for heroes to follow the path I'm marking.  They'll handle medical care for wounded.''



``That's fucked up,'' Rifle said.  ``We could at least put him out of his misery, then.''



``I'm not willing to get close enough to check,'' I said.  ``And I'm not willing for \emph{you} to get close either.''



``I--'' Parian started.



Then she stopped.  The fat man deflated in an instant as a small collection of what looked like trilobites found their way out of his rear end.  Slick with gore, they darted forward a short distance on their hundreds of little legs, then turned our way, bristling with spines.  Tails trailed behind each of them, twice as long as the foot-long creatures, narrow, with stingers on the ends.



I could hear a hissing, but I wasn't sure if it was from the creatures or the way the spines rubbed against one another.



``Oh\ldots god,'' she said.  She took a step back, with Foil stepping forward, as if to defend her.



``Breed's power,'' I said.  ``They're mostly harmless, for now.''



``For \emph{now}?'' Rifle asked.



I watched as they made their way up the side of a building to a corpse that was hung there.  The corpse had been cut into sections, the arms and legs each severed at the joints and reconnected with lengths of chain.  Breed's creatures found their way into the body through the holes in the neck, mouth and rear end.  It jerked a little as they worked bodies the size of footballs into apertures only a fraction of that size, then went still.



``For now,'' I answered Rifle.  ``They start off the size of a lemon, lurk in spots where they can get access to orifices or sites of injury, or like you see here, corpses.  Inside beer bottles, in toilet bowls, bedcovers, on the underside of kitchen tables, even inside food.  Then they burrow inside, wait until the target is still and quiet for an hour or two, \emph{paralyze} the target, and emit pheromones to call others of their kind to them.  They devour the target from the inside out, molt once or twice as they digest the fats and proteins they ate, then find a new target.  It's a process that takes a week to two weeks, depending on the availability of food sources.''



I could see Getaway shift position, folding his hands behind his back, as if he could shield his rear end.  His mouth had shut into a firm line.



His nose was still unprotected, I noted.



Even Rachel seemed a little concerned.  She glanced at her dog.



``They aren't a danger to us,'' I said.  ``Probably.  They choose easier targets over harder ones, and there are enough corpses around here that we aren't worth the trouble.  What we \emph{should} worry about is the later stages.  When they're about the size of a full-grown human being, they'll do two or three major molts with big physical changes, gaining some natural weapons, including a pellet-spit that kind of acts like a shotgun blast with fragments that dissolve into flesh-melting acid.''



``Um.''  Rifle said.



``You know this how?'' Imp asked.



``Read his file,'' I answered.



``Shouldn't we kill them before they get big?''  Foil asked.



``Not worth the time it would take to track them down,'' I said.  ``We don't have any strong offensive powers, they're durable against stuff like conventional ammunition and physical blows, and he generally produces about nine or ten per day.''



``That was ten,'' Getaway said.



``Even assuming it's only been one day since Breed woke up,'' I said, ``The scenes they've left behind suggest there are nine clones of each copy of the Nine.  Going by the numbers--''



``\emph{Twenty-nine copies, at least,'' }Revel said.



``Twenty-nine copies,'' I said.  ``Two-hundred-and-fifty-plus members of the Nine currently active.  Nine Breeds among them, meaning there're probably nine other clusters around here, taking advantage of abundant food.''



``\emph{Breed's creatures.  }\emph{Can you control them?}'' this from Revel, taking advantage of the stunned silence.



I glanced up at the body the things had invaded.  I tailored my response so both Revel and the Undersiders could make sense of it.  ``I can't control those things, and I can't sense them either.''



``\emph{A shame.  That would simplify things just a little}.''



It \emph{would}.  I wouldn't have minded the firepower, either, even with their particular diet.



``Let's keep moving,'' I said.  ``If we stop for every horror show, we might be stuck here a while.  My gut's telling me time is of the essence.''



``I'm feeling a little out of my depth,'' Getaway said, his voice quiet, as he fell into step to keep up.



``That's a good instinct,'' I replied without looking at him.  ``Trust it.''



``You're telling me to leave?''



``I can't make you do anything,'' I said.



``But you \emph{think} I should leave?''



``If you \emph{feel} like you should, yeah.''



``And does that extend to me and Rifle?'' Cozen asked, her tone cold.



``I don't know.  Yeah, if your instincts tell you to go, then get going now,'' I said.  I pointed at the ground around a hose.  There was a puddle that had spread beneath the hose's opening.  My bugs had died on contact with it.  ``Acid, not water.  Don't walk in it.  Rachel, watch your dogs.''



Rachel grunted acknowledgement.



``Don't change the subject.  You want us gone,'' Cozen said.



``No.  All the help we can get is appreciated,'' I said.  I glanced at her.  ``At the same time, if push comes to shove and you can't hold it together, it's going to hurt us all.''



``You don't think we can hold it together?'' Cozen asked.



``You're an unknown quantity.  Anyone else that's here, I can trust them to hold their own because I know how they operate.  I don't know you.  I don't know how you react in a crisis, how you'll respond if you're pushed to the edge, one way or another.  Grue and the others are vouching for you, so I'm shelving those concerns and trusting they have a good sense of your abilities.  I'll \emph{maintain }that trust until you give me an indication I shouldn't.  Getaway saying he's spooked is an indication.''



``\emph{I'm} spooked,'' Imp said.  ``Can I go home and sit on the couch in my underwear, eating cake?  I'll cross my fingers for you guys, if you want.''



``You're talking like you're in charge,'' Cozen said.  ``\emph{Grue} leads the Undersiders.''



``I'm not an Undersider,'' I said.  ``It doesn't matter.  I'm in charge anyways.''



\emph{And Grue can speak for himself}, I thought, but I didn't say it aloud.



I could see her reacting to that, even without the extra quip.  I watched expressions cross her face: irritation, anger, indignation, and a trace of fear.



``Grue is a good leader,'' I said, ``But this is \emph{my} project.  Something I've been working towards and thinking about for the last two years.  Leaving the Undersiders, making contacts, helping hold things together, maintaining the peace and eliminating possible issues.  Everything I did, it's been to prepare for this in some fashion.''



``A little unilateral, don't you think?''



``It's her project,'' Grue said.  ``My orders are to follow her orders.''



I could see how little she liked that.



But she maintained a professional demeanor.  ``Accepted.  You realize we don't have to follow your orders?''



Grue nodded, silent.



Cozen seemed to come to a decision.  ``We will anyways.  As Weaver pointed out, this is unfamiliar ground for us.  We'll defer to your experience.''



``Thank you,'' Grue and I said, almost in sync.



I turned away to hide my smile, in case it could be made out beneath the fabric of my mask.



Progress was slow.  The traps seemed to accrue in number as we drew closer to the center, as did the corpses.  More than once, we were forced to take the long way around, as traps or pools of acid barred our paths.



We passed an area with rows of identical looking cabins, then ran into the Protectorate.  Chevalier, Exalt, and others, examining the area, a block and a half away.



I got their attention, then pointed in the direction we were headed.  It wasn't much more effort to mark out traps around them as well.  I made sure to mark each with a cluster of bugs, and bug-letters spelling out the nature of the danger.  Less trouble to move in parallel directions than reunite.



The center of the spiral wasn't the center of the town in a \emph{geographic} sense, but in a sense of where the town's heart and focus were.  We closed in on the front steps of what looked to be a town hall.  Empty ski racks stood to our right, two draped with corpses that had been flung and broken over them.



By the time we were halfway through the plaza, navigating a maze where we tried to find a path that didn't force us to tread on potential traps or corpses, Tecton and the others had caught up, reaching the edge of the area.



``\emph{Thoughts}?'' Revel asked.  ``\emph{Before you reach the center of the display?}''



``He wanted to present this for effect,'' I said.  ``It's why he set up Pyrotechnical's stuff to blow any aircraft out of the sky.  The traps are to force us to take our time, force us to savor it.''



``Savor?'' Grue asked.



``Everything Jack does is for effect.  The same way a dog sort of raises its hackles to look bigger, tougher, or the way we used our reputation to seem more unstoppable than we were, Jack keys his actions for psychological effect.  All of this is to scare, to drive us to hesitate when it comes to confronting him, push us to think of ways to \emph{avoid} dealing with him instead of ways to catch up to him and beat his face in.  Or, conversely, some personality types might get pushed to be reckless, to deal with him so he couldn't bother them anymore.''



I glanced at Rachel as I said that last bit.  She'd instructed her dogs to stay, so they wouldn't trip any of the traps in our way.



I made my way over a hump of bodies.  The members of the Nine who'd spilled acid all over the place had melted nine police officers and left them in a heap.  Crawler?  Only one that fit.



Our destination was the kind of spot, like a courthouse's steps, where someone could give a speech.  There were two objects covered in tarps, a man who was in a reclining position at the far end of the stairs, and ten dead bodies arrayed in a star shape, limbs bent to mark the direction of the spiral.



I checked under the tarps, then bit my lip.



I turned around and gave Golem instructions as he made his way past the traps.  He created platforms to step over to serve as a shortcut.  Grace, Tecton, Wanton and Cuff hung back, looking grim.  They were joined by Chevalier and the others.



Golem joined me at the top of the stairs.



``How's your headspace?'' I asked.



``Terrified.''



``In a way that's going to impact our job here?''



``No.  No.  You told me what to expect.  Kind of.  I didn't imagine \emph{this}.''



I shook my head.  ``No.''



There was a voice from beneath the other tarp.  A strangled scream.



``What was that?''



``A recording,'' I lied.  Then I elaborated.  ``It's a trap.  Two tarps, have to guess the right one.  Guess the wrong one and you blow up.  This one.  Move the tarp.''



He hesitated.



``Trust me,'' I said.  \emph{Even as I lie for everyone's benefit}.



Rachel and Golem worked together to move the tarp aside.



A television.



``The tape's already in the machine, you can hit play to start it,'' the man sitting at the edge of the stairs said.



``\emph{Wait, Weaver, stop.  Who was that?}''  Revel asked.



``Who?'' I asked.  ``What do you mean?''



``\emph{Look to your right}.''



I did.  The other tarp, more corpses, the man who was now standing at the edge of the stairs, the little crenelation at the top of the stair's railing, then beyond that, cabins, restaurants, hotels and motels, the rest of the town, and mountains in the background.



``Not sure I get what you're saying,'' I said.



``What's wrong?'' Grue asked.



``I don't know.  I'm getting communications from Revel, and she's acting funny.''



``Here,'' the man said.  ``Let me get that for you.''



The others stepped out of the way as he approached me, Golem, and the television set.  He reached for the play button.



I caught his wrist.



``\emph{He's dangerous},'' Revel said.



``I beg your pardon?'' the man asked.



``\emph{Attack.}''



\emph{Attack?}



I shook my head a little, releasing the man's wrist.  ``I appreciate the offer, sir, but let's be safe and make sure this isn't a trap.''



``Can't argue with that,'' he said, smiling.



``\emph{This is what hell is like,}'' Revel said.  ``\emph{Listen to me.}''



``Tattletale, are you there?''  I asked.



``\emph{I am.}''



``\emph{Tattletale?}''  Revel asked.  ``\emph{Damn all of you.  It doesn't matter.  Listen, Taylor, Master and Stranger protocols are in effect.  Your perceptions are altered, understand?}''



I felt my heart quicken a little at that.  ``I understand.''



``\emph{There is a person to your right.  Not a teammate, former or current.  I need you to kill that person, don't ask why, don't think too much about it.  Draw your knife.}''



I drew my knife.



``\emph{Look.  I'll tell you who to attack.}''



I glanced to my right, my eyes falling on Rachel.  It was a bit presumptuous to say she wasn't a \emph{teammate}.  Not a team player, but she'd done her share.



``\emph{No, to her right.}''



I looked past the man and set my eyes on Golem.



``I'm more inclined to think \emph{you're} a voice in my head that's fucking with me, than to suspect Golem's up to something, but--''



``\emph{Oh hell},'' Revel said.



``\emph{I got this.  Taylor, do me a favor, give the order to `go dark'.}''



``Go dark,'' I said.



To my left, Grue surrounded himself in thick darkness.



Nothing happened.



``\emph{It didn't work}.''



``\emph{Wait}.''



A spray of blood leaped from the man's throat.  We each stepped away, and I hurried forward to stop Rachel from backing into the other tarp.  We watched in stunned silence as blood poured from the wound.



``Hey,'' a female voice said, ``Do me a favor, let me know if there are any traps at the bottom of the stairs?''



``Who--'' Golem started.



``Just tell me.''



``Acid,'' I said, raising my knife so I could defend myself if I had to.



Imp appeared as she booted the bleeding man in the small of the back.  He rolled down the stairs, leaving spatters and sprays of blood as he made his way down, and then collapsed in a pile of bodies.  He started screaming, a gurgling sound.



I could see Chevalier and the others staring in shock, adopting fighting stances, unsure of how to proceed.  It looked like Chevalier was talking to someone, gesturing with his free hand.  Was it Revel, on the comms?



``My schtick,'' Imp spat the words at the dying man.



I could mark the moment he died, because the blanks in my perception began to fill in.



\emph{Nice Guy}, I thought.  I'd badly underestimated the severity of his power.  I'd known he would be in their roster, had kept it in mind throughout, even told myself to be ready for him, and then the moment we ran into him, well, he was another face in the crowd.  The connection wasn't possible.



I watched as the acid ate away at him, burns creeping upward and spreading across his flesh, bubbling as it reached the cartilage of his nose and ears.



``\emph{Thank you, Tattletale,}'' Revel said.



``\emph{All good.}''



``\emph{I\ldots think I can tolerate your presence on this channel for the moment.  Provided you don't cause any trouble that makes me regret it.}''



``\emph{I'd do that anyways.  So.  One more trap down.  Keep in mind there are eight more of him.}''



``What was he going to do?'' Golem asked.



``\emph{Probably ask you all to stand there and stay still while he murdered each of you in turn,}'' Tattletale said.



``Oh.''



``Tattletale,'' I said.  ``Call my phone, and I'll put you on speaker.''



``\emph{Okay.  Let's see}.''



``\emph{Six-three-zero-five-five-}'' Revel started.



My phone rang.  I picked up and put Tattletale on speaker, as Revel sighed audibly in my ear.



``Is the video player safe?'' I asked.  I turned my head towards the television.



``\emph{Yeah.  All the rest of this, it's to scare.  It's also meant to delay.  Jack probably expected the heroes to take a little while to find this, to get by the traps.  The spiral you mentioned, it would have been maybe a day or two before they put the pieces together, then another three to six hours before they navigated it to the center.}''



``Yay us,'' Imp said.



\emph{She got more powerful}, I thought.  She'd been able to speak while using her power.  Nuances.



``\emph{Press play}.''



I hit the button.



It was Jack, here, in the center of the plaza.  The camera wobbled as someone followed him, recording.  I could see shadows of the other Slaughterhouse Nine in the background.  Hookwolf.  Skinslip.  Night Hag.



``This message is intended for Theodore Anders.  Kaiser's son.  Stop the video here and go find him.  Time is of the essence, I should say.  How much \emph{essence} and \emph{time} you have available depends on how incompetent you heroes are.  Hurry now, I'll wait.''



``\emph{No need to wait},'' Tattletale commented.  ``\emph{He's standing right here.}''



There were a few looks of surprise at that.  Eyes fell on Golem.



There was a pause, then Jack started speaking.  ``You missed the deadline, Theodore.  Simple game of hide and seek, and you had two years to do it, to find and kill me.  You failed.''



Golem's gloves made a small creaking sound as he clenched his fists.



``You remember the deal, right?  Two years to find me.  Two years, you fight past my minions, you look me in the eye, and then you kill me.  And if you fail?  A thousand people die.  Your sister joins them, and you're the last on the list.''



``\emph{Golem},'' Revel said.  She started to say something else, but Jack cut her off.



``That pain you feel, that self loathing?  The fear and dawning realization of what you've done?  \emph{Capture}\emph{that}, Theodore Anders.  Hold on to that feeling and use it, because I'm pulling your leg.''



Golem startled as if he'd been slapped.  His eyes had lowered, and now they returned to the screen.



``Circumstances beyond my control delayed me.  So \emph{I'm} going to do \emph{you} the favor of extending the deadline, and you're going to do \emph{me} the favor of forgiving my lateness.  Agreed?  Agreed.''



``Can we \emph{not} agree?'' Imp asked, uselessly.



Jack continued.  ``This is a \emph{prelude}.  See, all of these guys just woke up, and they needed a chance to stretch, flex their abilities and make sure everything works right.  Turn the camera around, Bonesaw dear.''



The camera panned around.  There were other members of the Slaughterhouse Nine present, standing in a loose half-circle.  Hundreds of them.  Nine of each.  Thirty groups.  I recognized most, could guess as to the others, who didn't have their powers or full transformations going.



In the middle of that semicircle, lying on the ground, civilians had their hands folded on the backs of their heads.  In many cases they'd been stacked like cordwood.  Many bound, others too terrified to move.



``Oh god,'' Golem said.



Jack spoke, his voice calm, clearly relishing this.  The camera returned to him, focusing on his face.  ``I promised a thousand bodies.  A thousand kills, if you failed to meet the challenge we set in our bargain.  Except there's a bit of a problem.  See, things have changed.  The Endbringers have apparently doubled down.  Terror is a fact of life.  As commodities go, this one has depreciated quite a bit in the time I've been gone.  We've \emph{really} got to step up my game if I'm going to pass muster and get on the front page of the paper, don't you agree?''



``No,'' Golem said.



Silent, I took his hand, holding it.  My eyes didn't leave the screen as I studied it for details, matching members of the Slaughterhouse Nine to the files I'd studied in recent months.



``Now, I'm still a man of my word,'' Jack said.  ``The original deal stands, of course.  That's why each member of my army here is going to walk away with three or four of the locals here.  We've whittled down the number to an even nine hundred and ninety-nine.  Let's say you have\ldots hmm.  Until the twenty-fourth.  Five days.''



We watched in silence.



\emph{What's the rub, the trick? }



``If you fail to kill me, I disband the Nine.''



``What?'' Imp asked.  ``\emph{What}?''



I frowned.  \emph{Not what I expected}.



``That's not an enticement to leave me alive,'' Jack purred the words, sounding pleased with himself.  ``See, Bonesaw did a very good job of putting my army together.  Each is in the prime of their life, fit, in fighting shape.''



``Aw shucks,'' a girl's voice said, offscreen.



``Their psychologies are close to what they should be, all things considered.  Except for tweaks, here and there.  I'm good when it comes to wrangling the wicked, but Bonesaw apparently felt two hundred and eighty would be too many, even for me.  She's made them loyal.  They'll listen better.  The most unpredictable and dangerous have been touched up, the edges rounded off.  While interacting with \emph{me}, anyways.  I won't sully \emph{your} experience on that front.



``No.  They're obedient and servile only when I require them to be.  If you fail in your task, then I'll give them one last task, to kill the one thousand people we agreed to in the terms of our wager, and then I'll disband the group.  They'll be free to run rampant, to do as they see fit.  Wreak chaos.  I'll take a vacation, sit back with a \emph{Mai Tai} and watch the show.''



``\emph{Fuck me},'' Tattletale said.



``Fuck,'' I echoed her, agreeing.



Golem, for his part, had gone stone-still.



``I'll be leaving members of the Slaughterhouse Nine behind at regular intervals as I beat a not-so-hasty retreat.  Your choice if you deal with them or leave them be.  But if I get \emph{one} report from them that you're getting help, one report that you're using others as a crutch, then that's it.  Order goes out, hostages die, Nine go off leash, and you get to watch the body count rise.''



``Five days, Theodore.  Noon on the twenty-fourth.  I look forward to meeting you.''



The video cut out.



``Tattletale?'' I asked.



``\emph{Already on it.  Word's going out to all the major players}.''



I noted Chevalier's approach.  He had used Golem's platform to reach the base of the stairs, stepping around Nice Guy.



``Major players?'' Grue asked.



``Everyone Tattletale's been meeting with,'' I said.



``I heard through the feed,'' Chevalier said.  ``The restrictions stand.''



``The restrictions stand,'' I agreed.  I explained for the benefit of the others.  ``We treat this as a Simurgh situation.  Control feedback, control exposure.  Anyone and everyone that potentially comes in contact with Jack could be a factor in Dinah's end of the world scenario.  Powerful individuals are especially important in this.  The more powerful they are, the more important it is to minimize or prevent contact.''



``Um.  I probably sound dumb as I ask this,'' Imp said, raising a hand as if she were asking a question in class, ``But what about the nearly-three-hundred lunatic psycho people with crazy powers that he's threatening to unleash on the world?''



``We'll deal with them,'' I said.  ``With your okay, Chevalier?''



He fell silent.



``Chevalier, I thought--''



``Yes.  You proposed your strike squad. You've shown their ability to deal with different situations.  Fine.  But I'm assigning two tertiary squads to you.''



``Chicago and Brockton Bay teams.''



``I was going to say--''



``They're teams I'm familiar with,'' I said.  ``Please.''



He fell silent again.



``Work with me here, and if we're all standing at the end, I'm yours.  Whatever you want to use me for, however, it doesn't matter.  If this blows over and the end of the world doesn't happen, like some think it won't, then the deal stands.''



``I'll get in contact with Miss Militia and Crucible.''



``If it's alright, can we have Clockblocker take control of the Wards for this excursion?''



``Whatever you need,'' Chevalier said.  ``You realize we're pinning a lot on you?''



``On Golem more than me,'' I said.  ``We're going to cheat our way through this, bend every rule, but it all hinges on Golem being able to hold his own.''



``\emph{Jack's going to try to set Golem up with a long chain of lose-lose situations,}'' Tattletale said.  ``\emph{Force him to either let the innocents die and maintain the chase, or let Jack pull away.  We already got one big advantage by getting to this tape as fast as we did.  Let's not show our hand.  Dragon's on the line.  We've got Dragon's Teeth and Azazel models moving to the front.}''



``Close in the net, then act decisively,'' I said.  ``Coordinated strikes.  If the \emph{Thanda} are willing, a meteor strike in the right time and place could do wonders.''



There were nods of agreement from around the group.



Golem turned around and walked away.



``Golem,'' I said.



He was already halfway down the stairs.  He used the panels at his waist to form an even footpath, with hands turned at right angles, positioned where he could put his feet on them.



``Golem!'' I called out.  I handed my phone to Grue, then hurried after him.



He stopped as he set his foot on the first outstretched hand of pavement, but he didn't turn around.  His voice was low, barely a whisper.  ``Stop, Taylor.  Leave me alone.  Please.''



``You're \emph{running}?''



``I'm\ldots no.  I'm definitely in.  I have to be, don't I?''



``But?''



``But this is a lot to take in.  Jack, he talked to me about ripples.  About stuff extending outward, the lives that are affected.''



``I remember.  You told me that.''



``Right here, in this dinky little ski resort, he murdered a few hundred people, just as a \emph{warm up}.  How many people on the periphery of it all are affected?  How many people across America, across the \emph{world}, know people in Killington?  Or know the people who know people in this town?''



``You can't think about things on that scale.''



``I have to.  Jack does, and I have to understand him.  If I \emph{don't }pay attention to it, if I ignore it all, pursuing only the end result, the target, then I'm acting like \emph{my dad}.  Kind of.  Either way, I lose.''



``You care about the people who died, and you're thinking about them that way for a good reason.  That's not putting you on a path to being like either of them.''



``But that kind of consideration, letting it \emph{really} sink in, it eats away at you, doesn't it?  \emph{Shouldn't} it?''



``It should,'' I said.



``There's a reason we go numb, and I get that, but I don't want to go down that road, not so quickly.  Not knowing just how easy it would be to \emph{revel} in it, or to stop caring about the dead.  I'm there, and I'm\ldots''



``What?''



The stoic face on his helm stared down at the ground.



``Theo?''



``I hear you guys talking about it, and you're right there\emph{, }in your element.  This is something that you've been working on for a long time, and there's almost an excitement to you.  Like you've been in a kind of stasis for the entire time I've known you, and only now are you really coming back to life.''



``It's not like that,'' I said.



``No.  I mean, I'm not blaming you, or saying you're a bad person.  You're good at this, at taking a challenge head on, finding workarounds, manipulating the system to our advantage.  You're doing it for good reasons, to help, to stop bad people.  I saw glimmers of that excitement, of the \emph{real} Weaver, while you were dealing with our bosses, and making connections, offering deals to the bad guys you thought you could bring to our side.  But I've spent a long time thinking about Jack and watching old footage of him, and figuring out my enemy, my nemesis, and it's like\ldots that's \emph{you}.''



``Me.''



``\emph{You're} his nemesis, Weaver.  \emph{I'm} the reason he's here, the reason these people died like this.  But you're his counterpart, his mirror.  You've got that same excitement Jack has, you think along the same lines, in strategy and counter-strategy.  You \emph{thrive} on conflict, just like he does.  And I\ldots I'm not like that.''



I couldn't muster a response.



``So right now?  You should go back.  Forget I said this, because it's\ldots I'm regretting opening my mouth already.  Work on formatting the strategies you already worked out to fit around the rules of Jack's \emph{game}, because that's a \emph{good} thing.  It's what we need.  But let me have half an hour or an hour or however long I need to myself.  Until we stop waiting and stop letting Jack think we haven't found the tape yet.  Let me take a moment and think about these people.''



``You're not to blame for them,'' I said.  ``The Nine would have killed anyways.''



``I know.  I get that.  But I played a part in the sequence of events, and maybe \emph{these} people wouldn't have been the ones to die if I hadn't made that wager with Jack\ldots and I guess I think everyone else that cares has better things to do.  You trained me, the others trained me.  I- I guess I'm as ready as I could ever be.  I'll fight when the time comes, wade through the gauntlet he sets in his wake and I'll succeed or fail.  But I'm not a strategist, and these people need someone to mourn them.  Let me be useful in my own way, right here, right now.''



I opened my mouth to voice a reply, then shut it.



A moment passed, and Golem set about walking on the hands he'd raised from the ground, just two or so feet above the bodies and the streets that were painted with blood.



I stood where I was, watching as he steadily made his way to the safe zone I'd drawn out on the ground.  He stopped only to gesture for Tecton and Grace not to follow, then walked on, out of sight.



\emph{It's not that I don't care}, I thought.  \emph{But-}



\emph{But what}?



I couldn't articulate my thoughts.



\emph{But\ldots we need a strategist}, \emph{we need a plan, before all hell breaks loose}, I thought.  \emph{Developing that, coming up with answers, fighting, it's going to do a lot more good in the long run than compassion all on its own}.



I looked down at Nice Guy, at the foot of the stairs, a fleshy mess that was slowly dissolving into the acid pile, which only spread and served as \emph{more} acid to melt flesh.  I realized I was still holding my knife, from the time of the brief skirmish.  I sheathed it.



Then, as Golem had told me to, I pushed him, the dead, the maimed and the lost out of mind and turned back to the core group, to offer my services, to coordinate and administrate.





