





It started at the center of town, a rolling plume of fire, sparks and smoke that seemed to almost \emph{lurch} skyward, in fits and starts.  Each set of charges that went off pushed the flame up through the smoke of the ones that had come before.



Then the charges around the perimeter of the city went off, each focused inward.  The rolling mass of fire and superheated air at the center of the city shot through the cloud cover, and the entire sky turned colors.  Reds, oranges and yellows, interlaced with the gray and near-black shadows of the smoke.



Killington was officially gone, the buildings leveled, the bodies and bloodstains scoured from the earth.  Families wouldn't get to put their loved ones to rest the way they wanted, but that was on the Nine, not on us.  There was no safe way to recover the bodies, to ensure that there weren't any traps or time delayed tricks in each and every one of the corpses.  It also meant Breed's minions were torched before they reached an adult stage.



The area would be marked off for a duration after this, in case there were any heat-resistant bacteria or the like.  Cheap, prefabricated walls would seal in the area, and roads would be put in to allow people to make detours.



\emph{Quarantine,} I thought.  Every step of the way, we had to be on guard.



It was time to move on.  I looked to the book in my lap, turned down the corner of the page to mark it, and then stood, stretching.  It was a nice spot, a long porch just outside a cabin, one that was probably rented out at a premium price during the skiing months.  Far enough away to be safe, high enough to serve as a vantage point while letting me reach to the necessary areas with my bugs.



The entire porch was layered with pieces of paper, organized into rows and columns with some overlap.  The edge of each paper was weighed down by a mass of bugs, almost insufficient as the hot air from the quarantine measure blew past us.  Millipedes that had been moving across the various pages remained still, striving only to stay in place.



The moment the wind died down, I bid the bugs to shift position, carrying the pages to me, sorting them into the appropriate order.



I bent down and began collecting the pieces of paper.  I could feel the raised bumps on the pages as I brushed them free of specks of dirt and leaves.  Each set of bumps corresponded with a letter or punctuation mark, which had been printed over the dots in thick, bold, letters.



I gathered the pages into file folders, then clipped them shut, stacking them on the patio chair.  I made my way to the patio table, bending down to collect the pages as they made their way to me.  The writing on these was different; the letters were drawn in thick, bold strokes, fat, almost as if I'd drawn them in marker.  My notes: thoughts, things that needed clarification, ideas.



At the patio table, I took hold of a beetle and used its pincers to pick some petals out of the shallow bowl, grabbed the caterpillar I'd been using as a brush, then tossed the two bugs over the porch's railing.  I tipped the ink from the bowl back into a small jar, then screwed it tight, sliding it into a pocket at the small of my back.



I was still getting organized when Defiant appeared, ascending the stairs on the far end of the porch.



``Quite a view,'' he commented.



I looked at the resort town.  The fire hadn't yet gone out.  It was flattening out, scouring everything from the area.



Almost everything.  One or two things would remain.  Probably until well after the sun went out.



``Pyrotechnical's stuff?''  I asked, distracting myself.



``And some of Dragon's.  Are you ready to go?''



``I'm ready,'' I said.  I picked up the files, then passed them around behind me, where the arms of my flight pack pinned them in place.  I was left with only the book to hold.



He walked beside me as we made our way down to where the craft had landed. His suit had been augmented and altered, and he now stood a foot and a half taller than he had when I'd first met him.  Broad `toes' on either side of his boots helped stabilize him, while his gloves ended in clawed gauntlets that extended a little beyond where his hands should be.  His spear was longer, and both ends of the weapon were heavy with the devices he'd loaded into it.



On his forearms, shoulders and knees there were panels that were like narrow shields, each three or four feet long, each marked with designs like a dragon's wings, or with a dragon's face engraved on the front, mouth open, with red lights glowing from within.  Wings on his back served less to let him fly and more to accentuate his movements, a more complex, bulkier system than I had with my flight pack.  Then again, I was only a hundred and thirty pounds at five feet, ten inches in height, and Defiant must have weighed six hundred pounds, with all that armor.



I'd seen him fight Endbringers in that suit, seen how he could move as fast as anyone who wasn't a speedster, turning his spinning weapon and those shield-like extensions on his armor into a whirling flurry of nano-thorns, cutting through seventy to eighty percent of the Endbringer's flesh before they reached material too dense to penetrate.



Which was when he'd use his other weapons.



I envied him a little, that he could take the fight to the enemy like that.  We were similar, on a lot of levels, but we differed on that front.  On a good day or otherwise, I'd never be able to truly \emph{fight} an Endbringer.  I had to depend on others.  The best I could do was coordinate.



``The moment you or one of your teams lets something slip, this falls apart.''



``I won't fuck up.''



``You will.  Or someone working under you will.  You're good, but we can't account for every contingency.  Something's going to go wrong at some point.  The later that occurs, the better.''



``Yeah,'' I responded.



``Every minute that passes is a minute where we can gather information, close in on Jack and figure things out.  We've got a lot of good minds and good eyes working on this, but there are a lot of bases to cover.  We let Golem get close, mop up everything we can and contain everything else, and then we take Jack down.''



I nodded.  ``But we don't want to stand back and wait when people could be hurt, or when every second that passes is a second that Jack could be making contact with that critical person.  Causing a certain trigger event, saying the wrong thing to the wrong individual\ldots''



``There's a balance.  I trust you'll find it.''



``I hope I can,'' I said.



We'd interacted less and less in recent months, and those interactions had been short and to the point by necessity.  It didn't hurt that the two of us weren't terribly social people.  We didn't revel in small talk.  We \emph{could} be adroit when circumstances forced our hands, but we could also stumble, say things in a way that was just a little off, or give the wrong impression.



I \emph{liked} that we had a professional relationship, that we didn't have other stuff getting in the way.  No pleases and thank yous.  We both knew what was at stake, we were on the same page, and we were doing what we felt we had to in order to get the necessary shit done.



``I spoke with Alcott,'' he said.



I drew in a breath, then sighed.  ``What does she say?''



``The numbers haven't changed dramatically.  The window's closed, but not considerably, which suggests a lot of things.''



``Okay,'' I said.



``Ninety-three point eight percent chance the world ends,'' Defiant said.



\emph{Up from Eighty three point four percent}.  \emph{That's not considerable}?



``She's done us the favor of plotting the changes in the numbers over time.  When things stabilized for a considerable length of time, she scaled down from noting the numbers twice a day to noting them once.  Eighty-three point four percent, as of the beginning of the crisis in Brockton Bay, the Nine's attempt to test and recruit new members.''



``I remember,'' I said.



``Eighty-eight point six percent after they escaped the city.  It was quite possibly our best opportunity at killing Jack, and we missed it.''



I frowned.



``With each destination the Nine reached after Brockton Bay, the numbers shifted, and not for the better.  Half a percent here, two percent there.''



``Chances where someone \emph{could} have theoretically killed him but didn't.''



Defiant nodded.  ``We ran things by the thinkers, and that's the general consensus.  Low chances, but he had the Siberian with him up until the fight in Boston\emph{.}''



The same fight where Dragon and Defiant had taken on the Nine, and the Siberian had been killed.



``We had one opportunity there.  That failure is on me.''



He turned his head slightly, then amended his statement.  ``On us.''



I didn't disagree.  Denying that would mean denying my own responsibility in failing to kill Jack in Brockton Bay.



``Ninety-three point eight,'' Defiant repeated, for emphasis.



``Six point two percent chance we'll pull this off,'' I said.



``It remains tied to him.  If we kill him in the next ninety hours, the chances vastly, \emph{vastly} improve.  Depending on \emph{how} we kill him, it could mean reducing things to a mere twenty-two percent chance or a one percent chance.''



I nodded, making a mental note.  ``Theoretically, if we nuked the northeast corner of America\ldots''



``Only a sixty percent chance of working, with some decimal points that Dragon's urging me to include as I speak, and a high chance we set things in motion anyways.  Twenty eight or so.''



\emph{He asked Dinah}, I thought to myself.  \emph{The same question I had in mind, give or take}.



There were clues there.  ``A nuke won't kill him for sure.  Bomb shelter?''



``Possible.  Or he's keeping Siberian close at hand.''



``And whatever role he plays\ldots he greases the wheels, he doesn't guarantee it.  You're saying there's a chance things get set off even if he dies.  If that doesn't happen, then there's some point in the future, roughly fourteen years from now, where things get set off anyways.''



Defiant nodded.



``Every time I think about it, I can't help but think it's a trigger event,'' I said.  ``Someone getting a power that finally \emph{breaks} something essential, or a power without the limits that keep other powers in check.  But I don't want to think along those lines if it keeps me from seeing the obvious.''



``Sensible.  But let's not dwell on it.  The thinkers are handling it, as best as they can, and \emph{we }have to devote attention to this crisis.  We've got all of the big guns lined up.  The moment things fall apart and Jack decides the rules of his game, Dragon is going to try and jam communications, and each of us moves in for a quick decisive victory over the members of the Nine on site.''



I nodded.



We were just arriving at the perimeter of Killington.  I could see some of the big guns Defiant had been talking about.



Two Azazels had set up thick hedges of that blurry gray material just behind the barriers the heroes had erected to protect themselves and contain the fire.  I also saw the Dragon's Teeth.



Soldiers was the wrong word, but it was close.



Each wore armor in gun-metal and black, with parallels to the standard PRT uniforms I was more familiar with.  Their helmets, however, had three eyeholes, with blue lenses glowing faintly from beneath.  Two lenses for their eyes, a third for a camera.  The armor was bulky, offering thick protection around the neck and joints, with a heavy pack on the back for both oxygen and for the computers they wore.



They were, in large part, wearing stripped-down versions of Defiant's outfit.  Sacrifices had been made to account for the fact that their suits didn't render them seven and a half feet tall.  Each carried a sword and a laser pistol.



I'd never liked the cameras.  Heads turned as I approached, and I knew they were recording, tracking details about me and feeding them back to a main server, where they compiled information, discarded excess.



The combat engines that the Dragon's Teeth were wearing were still in early stages, the data patchy, depending on the target.  The people in uniform had spent weeks and months training with the things, learning to shift fluidly between their own tactics and awareness of the situation and the data that was provided.  Protectorate Capes and Wards that were just starting out were being trained with the things, but those of us that had experience fighting tended to find them a distraction.



Useful?  Yes.  A bit of a boost, a bit of an edge.  But not quite at the point where \emph{everyone} could benefit.



Not yet.



Not that there was much room for developing any of it if the end of the world went ahead on schedule.



I could see Narwhal, standing off to one side, two of the Dragon's Teeth flanking her.  Masamune wasn't present, but from what I knew of the guy, he wasn't even close to being a front-lines combatant.   They'd recruited him from the ruined area of Japan, a somewhat crazed hermit, and gave him work in figuring out how to mass produce their stuff without the maintenance issues snowballing out of control, like tinker tech tended to do in large quantities.



Thanks to him, they had the Dragon's Teeth, they had the combat engines and they had top of the line gear for various members of the Protectorate and Wards.



Of the other members of the Guild, the only other one who could theoretically be on the front lines of the fight would be Glyph.  I could only assume she was somewhere close.



The \emph{Thanda} weren't here.  If Dragon had managed to get in touch with others, they hadn't yet arrived.  I could only guess as to what Cauldron might be doing.  Faultline's crew, the Irregulars\ldots



Too many maybes.  With Endbringers attacking every two months, a lot of people were busy reeling from recent attacks or preparing for the next.



I looked at the assembled capes.  The Undersiders, two Wards teams, the Protectorate, the Guild.  Clockblocker, Vista and Kid Win were in the other Wards team.  A little older.  Clockblocker had expanded his costume, adding some light power armor that seemed primarily focused on holding a heavy construction at his back.  Vista, for her part, was a little taller, her hair longer, tied in a french braid that was clipped just in front of one shoulder. She was packing a heavier gun.  Probably something Kid Win had made.



And Kid Win was hardly a kid anymore.  I hesitated to call him a teenager, even.  His rig looked like it packed more artillery than any of Dragon's craft.  No neck, no arms, he barely looked capable of walking.  Just two stumpy legs, a simple gold helmet with a red pane covering his face and enough gun nozzles that he looked like a hedgehog.



``This is probably the last time we'll all be standing here together before this ends,'' Chevalier said.  ``I won't do a big speech.''



He turned his head to take us all in.  ``I've done too many of them over the past two years, I'd only repeat myself.  Everyone here knows what we're here for, why we're doing this.  We've talked this over with each of you in turn and you don't need convincing, you don't need a reminder of what's at stake.  You already know the role you're going to play in this.  Words aren't going to change any of that.  Good luck, be proud, and maybe say a little prayer to God, or ask for a little help from whoever or whatever you believe in.''



The instant he finished, the Azazels and other Dragon-craft began opening up, doors sliding apart and ramps lowering.



``The one time I do show up for one of these things, and no speech.  I feel gypped.''



I didn't see who had muttered the comment, but I could guess it was Imp.



``No dying,'' I said, as everyone started moving.



``No dying,'' others echoed me.  The voices of the Undersiders and the Chicago Wards were loudest among them.



My teams gathered in the Dragonfly, while the Chicago Protectorate and Brockton Bay Wards made their way to Defiant's larger ship, along with a contingent of the Dragon's Teeth.



Golem stood apart, until my ship was nearly at full capacity.



``It all comes down to this,'' he said, as I joined him at the base of the ramp,  ``All the training, all the planning and preparation, studying about the Nine backwards and forwards\ldots''



``Yeah,'' I responded, as I stepped up to stand beside him.  Our teams were getting sorted out, finding benches and seats.  I reached behind my back to get the file folders I'd brought with me.



``I'm sorry if I was harsh yesterday.''



I shook my head and reached out to put my hand on his shoulder.  It was support, and maybe a bit of a push.  He made his way up the ramp.



Stepping inside just behind Golem, I used the same controls that managed my flight pack to indicate that the ship could close the door.



The Chicago Wards had seated themselves on one side of the ship, the Undersiders on the other.  Something of a mistake, that, because it meant they sat facing one another as we made our way to our destination.



A little awkward.  I sat with them behind me as I took the cockpit.  The thing flew itself, but it freed me to focus on other things.



Chevalier had talked about making peace with the powers that be.  I frowned, staring at the control panel as the ship lifted off.



\emph{Passenger}, I thought.  \emph{Been a while, trying to figure out how to make peace with the fact that you're there, that you're affecting me somehow, taking control whenever I'm not in my own mind.  I think we've made strides.  I've sort of accepted that you're going to do what you're going to do, whether that helps me or hurts me.  }



\emph{So maybe, just maybe, you could help me out today.  Whatever it is you do, whatever motivates you, I can continue to play along, but I need a bit of backup here}.



My eyes fell on the bugs that crawled on the back of my hand.  Not even a whisper of a movement.



\emph{Yeah, didn't think I'd get a reply.  Guess we'll see}.



The ship's acceleration kicked in, and the bugs took flight.



\blacksquare



My eyes scanned the screens in front of me.  I had camera feeds from Clockblocker and Revel, from Chevalier, Imp, and the airborne Azazel.  They all focused on a single area, each from a different direction.



A thick white mist lingered throughout an area.  It was early in the morning, and that might have played a role, but there were no people.  Even for a smaller city like Schenectady, that wasn't so usual.  At nearly eight in the morning, there should have been people leaving for work, people running errands.



Desolate.  White fog.



``Winter's here,'' I said, speaking over the comms.  ``Others to be confirmed.  We've talked about this one, Golem.''



I turned the computer off and strode out of the ship.  Rachel was waiting for me outside, standing guard with her dogs and her wolf.



``\emph{Winter means Crimson too, doesn't it?}'' Golem asked.



``Probably.  Probably means-``



\emph{``}We see you,'' The words were like a whisper, barely audible.  \emph{``}See you standing there.  Oh, I do hope you're not Theodore.  Tell me you aren't, because it means we get to play all we want.''



``Screamer,'' I informed the others.  \emph{Early Nine member, psychological warfare, pressure, distraction.  Sound manipulation.}  Her power meant her voice didn't get quieter as it traveled great distances.  That wasn't the full extent of-



``Nice weapon,''  Her voice sounded in my ear, at a normal speaking volume.  I didn't flinch.  I could sense my surroundings with my bugs, and I could \emph{hear} things with them, hear how the sound panned out in a weird way over the entire area.



``You've got friends, Theodore.  I sure hope they aren't planning on helping you.''



It was a sinuous sound, seductive in how convincing it was.  Every time she spoke, she sounded a little more like me.  It would be the same for the others, hearing themselves.



She was somewhere in the area.  The question was how she'd gotten a sense of our voices so quickly.  There was supposed to be a limit to how quickly she could pick up on that stuff just from overhearing us.



``\emph{Confirm, team leader},'' Golem said, over the channel.  ``\emph{And can we use the password system we talked about?}``



``Queen.  Password system is a go.  What do you need confirmation on?''



``\emph{Ring.}\emph{Enemy headcount.}``



``Stag.  No headcount given, I think that's Screamer fucking with you.  Others include Winter, probably Crimson, and probably Cherish, if she's finding us like she is.  All allied capes, be advised, we're putting passwords into effect.  Stay calm, don't panic.''



``\emph{I do like it when they make it challenging},'' Screamer's whisper hissed in my ear.  It had changed in tone, pitch, cadence.



The Dragonfly took off as I made my way closer to the site.  \emph{Outside} of the area, there were people reacting.  Some fled, others were taking cover, followed by disparate voices.



``\emph{Haymaker.  I'm engaging,}'' Golem said.  ``\emph{Recommendation?}``



Screamer interrupted, ``\emph{Getting advice is against the spirit of this challenge, isn't it, Theodore?  You are Theodore, aren't you?  I think you should confirm for us}.''



``Mantis,'' I said, voicing the password,  ``Don't respond to her.  It's what she wants.  Take out Cherish ASAP, if she's here, Screamer after that.''



``\emph{I'm hurt}.  \emph{I rate second after the new girl who barely lasted a month?}``



``\emph{Have to find them first},'' Golem said.



\emph{I'll help with that}, I thought.  Then I stopped.  ``Golem, the password?  Horsefly.''



``\emph{Steeple.  And gauntlet}, to reply to the last one,'' his voice came over the comms.



I stopped.  We'd agreed on a simple password set.  There was a pattern, each corresponding to our powers and the various pieces on a chessboard.  Mine were related to bugs, his to hands.  It was abstract, something that tended to only make sense in retrospect.  The chess ones we knew off by heart, because they were the first ones we'd practiced.



And steeple wasn't one of them.



``Steeple?'' I asked.



``\emph{I'm drawing a mental blank,}'' Golem responded.  ``\emph{It works, doesn't it?  Pinkie.}``



Screamer wasn't stupid, but was she \emph{that} smart?  The `stag' should have thrown her off regarding our pattern.



``It works,'' I said.  ``Ant.\emph{  }I'm close.''



If that \emph{was} Golem, he wasn't as focused as we needed him to be.



I could feel the effect as my bugs entered the radius of Winter's power.  She wasn't concentrating it, so it was mild at best.  Slowing the movements of molecules, cutting down the ambient temperature, to the point that the moisture in the air froze.  It also affected my bugs.  Torpor.



For anyone within, it would include a \emph{mental} torpor.



If the only members of the Nine who were present were Crimson, Winter, Cherish and Screamer, then this was a fight that involved \emph{attrition}.  Attacking Russia in the wintertime.  Psychological warfare, emotional warfare, the effects of Winter's power\ldots it meant that Winter's guns and Crimson's power were the only \emph{physical }threats.



They were going easy on him at the outset.



Golem was walking on rooftops at the edge of the effect, and he was surrounded by a nimbus of whirling material.  By Wanton.  We'd already altered all of the data on the group, to imply by news reports and Golem's powers on the websites that Wanton's telekinetic storm was \emph{Golem's} power.



The vantage point put him high enough that he could stand above the mist without being \emph{in} it.  From the moment he engaged, he'd have to move fast.  He'd have to be indirect-



``\emph{Weaver},'' Golem said, interrupting my thoughts.  ``\emph{Iron fist.  She's offering to tell me where Jack is.}``



``We expected this,'' I answered.  Iron fist was the `king' in our chess sequence of passwords.  \emph{``}Crab.  Get the info and go.''



``\emph{I'm not that foolish},'' Screamer whispered, her voice extending throughout the entire area.  ``\emph{Underestimating me, for shame.  I give up the information, and you leave me for your clean up squad to execute}.  \emph{I want concessions}.''



``\emph{Concessions?}''  Golem had left his channel open.



``\emph{Let's ensure your friends aren't in a good state to mop up.  We'll start with this Weaver.  Why don't you cut off your toes, Weaver?  Keep you from running after us.}``



I frowned.



``\emph{Oh, you've got an alternative?  Something you can cut off or throw away?  Yes.  Let's put off the self-mutilation and have you throw that off the edge of a building.}``



Chances were good that she was in Cherish's company, getting information from the source.



``\emph{What if she tosses it, then walks into the mist?}'' Golem suggested.



No, not Golem.  \emph{Her.}  Screamer.  An easier suggestion to acknowledge if I thought it came from a teammate.



``\emph{Not buying it, huh?}'' he asked.  \emph{She} asked.



She'd narrowed down my location, was refining her voices.  That had been convincing.  I had to move, make it harder for her.



I advanced, but I didn't step into the mist.  The closer I got, the more of the affected area I could sense.  The torpor forced me to be efficient, to manage where bugs went and how, to check areas in a cursory way.  There were a number of people still in Winter's area of influence.  People were standing utterly still, slowly dying as the cold ate away at them.



\emph{I want to kill myself}.



My own voice, indistinguishable from the one in my head.  Fuck me.  She had a bead on me, now.



\emph{It'll be painless, a way to avoid all of the horror, so I don't have to watch my friends die.  So I won't have to watch Bitch or Tattletale or Imp die the way Regent did}.  \emph{So I don't have to watch Grue die.}



No, a moment's consideration and the spell was broken.  I'd stopped thinking of Rachel as `Bitch' some time ago.



``\emph{Aw},'' Screamer whispered.  ``\emph{Golem's refusing my deal, and Cherish says you're not playing along with the rest of it, so I'm gonna have words with some of the others}.''



I raised a hand to my ear, opening my mouth to warn them, ``\ldots''



My lips moved, but my voice didn't come out.  Bare whispers of sound formed, instead, even as I raised my voice to a near shout.



That would be the next stage in her tactics.  Isolate.  She had a sense of my voice, the way I spoke, and was canceling it out.



I signaled Golem with my bugs.  I drew a smiley face in the air with my bugs, crossing out the mouth with an `x'.



He nodded.



So he was on mute as well.



\emph{There}.



In the midst of a small duplex, there were two young women huddled together on an upper floor.  There were computers arranged around them, and each was playing a different video.  In some cases, it was the same video playing, just from a different point in time.  Me in the lunchroom with Defiant and Dragon.  The New Delhi Endbringer fight.  Golem on the news with Campanile.



She had to be almost as good a multitasker as me to take all of that in.



``\emph{Tattletale here.  Wormtongue}.\emph{  Doing damage control}.  \emph{I've got your video feed, so you can spell things out for me if you want to give the signal.}``



I spelled out the word `thanks'.



My bugs had died inside the area of cold.  The people inside wouldn't be doing much better.  I had to send another batch in.  This time, I knew the destination.



Cherish was acting as the eyes, Screamer as communications.  No doubt Screamer -all \emph{nine} of the Screamers- was providing communications between this group and the nearest group of Nine.  She was talking, in a low and steady voice, but her voice wasn't more than a murmur.  No doubt someone in a more distant location was receiving the intel at a normal volume.



And all of that raised the question of what Winter and Crimson were doing.  I scanned the building.  Nothing on the top floor, or the next lowest.  Further downstairs, a number of people were in the sway of Winter's power, their thoughts slowed to a crawl.



The basement of the same building.  Winter, Crimson, and their hostages.  Some would be the ones from Killington.  Others were ones that had fallen into the sway of Winter's torpor.  Crimson was feeding on them.



His schtick was a little bit of a vampire one, but the end result was more Mr. Hyde.  Big, muscular, fueled by rage and impulse.



The ones lying on the floor, cold, they'd be dead already.



I spelled out basic instructions for Golem, pointing the way to the building, drawing a cloud over the building to mark it.  He gave me a thumbs up.



Another arrow pointed him to the concrete rooftop behind him.  There, I drew out a basic layout.



And in that same moment, Cherish cottoned on to what we were doing.



``They're attacking,'' Cherish said.



Screamer's voice reached all of us.  ``\emph{Cocky, cocky.}``



Screamer turned her head, swatted at the bugs that crawled on her face, and then spoke, silent to the insect's hearing.



Winter and Crimson reacted.



\emph{Sure hope your boy can fight.  }Screamer was talking in my head again.  Not telepathy, only hearing a voice that sounded damn close to the one in my head.



``Fuck off, Screamer,'' I muttered.



``Grue no!'' Imp's voice.  I flinched despite myself, before I remembered they weren't anywhere nearby.



Screamer laughed, her voice floating through the area.



Crimson made his way outside.  His flesh would be engorged, purple-red, the veins would be standing out.  He'd be as hard as iron, strong.  His sword was as long as he was tall.  I couldn't get a good measure of its appearance or quality.



Winter hung back with the hostages.



I wrote out the information with bugs.  Tattletale relayed it.  ``\emph{Crimson Incoming.  Quisling}.  \emph{Got confirmation and you're good to go. }\emph{Six stories, elbow deep.}``



Golem turned his head, no doubt in response to the warning, then turned back to my diagram.



I'd given it a title, words running along the top.  `Slap them down.'



Golem's uniform was roughly the same as the early incarnations, though solidified into a more solid color scheme, dark iron and silver.  The materials differed, but it matched.



There had been one or two additions, though.  The rigging of different panels included a frame that looped over the shoulders, much like a rollcage.  Golem paused, then drew out a panel, attaching it to the right.  He began to reach inside.



And a hand emerged from the center of the street, large enough that it could hold a car inside it.  Crimson paused as he watched it appear.



Then he moved.  It was the kind of movement that came with super strength, a bounding, powerful stride that could have carried him through a wall.  He had to pause before he reached the base of the building Golem stood atop.



The hand had emerged up to the second knuckle.



``\emph{Abandon the fight},'' Tecton's voice.  ``\emph{Run!  Move!  }\emph{You've got six Siberians headed your way}.''



No password?



``Tecton, confirm.''



``\emph{Confirm what?}``



And a chuckle from Screamer, just in my ear.



Crimson ascended, climbing the outside of the building while holding his six-foot blade in his teeth, blood trickling down from the corners of his mouth where the blade was cutting into flesh.



My bugs died of the cold before I saw what happened next.  I was forced to send in a second wave to see.



The bugs were too slow, but the upper edge of the roof was outside of Winter's realm of influence.  I could sense Golem reaching out with a hand of brick, a gentle push on Crimson's collarbone with his left hand, pushing him away from the roof, away from any point where he could get a grip.



Crimson reached out and up for the hand, but the material broke apart as he put too much weight on it.  He dropped.  I'd bemoaned the effectiveness of rooftop combat, but Golem made it his own.



Golem advanced to the edge of the roof and created more hands, trying to bind the villain to the street.  An arm lock, a headlock\ldots



Crimson pulled his way free of the asphalt shackles through sheer brute strength.  More appeared, but he destroyed them faster than they could be created.



Screamer and Cherish had to know what we were doing, yet they weren't moving.  Cockiness?



No.  They had to have an escape route.



Except they didn't have a teleporter.  That left only a few options.  Siberian wasn't one I could do a whole lot about, but she'd be fighting if she were anywhere nearby.  The others\ldots



I drew out silk thread in their direction.  Only so much to spare.  I knotted it between their necks and the computers that surrounded them.



Theo's massive hand was still growing, the wrist exposed.  Almost halfway there.



Crimson ascended the building once more.  This time, he had support.



Together, we'd gone over the various members of the Nine, past and present, we'd detailed battle plans, the techniques we knew about, even contacted heroes who had encountered them in the past, for stuff that might not have gone on record.



But Screamer was called screamer for a reason, and there wasn't a lot we could do to stop it, not unless we wanted to deafen ourselves.



Crimson was three stories up the side of the building when Screamer used her namesake power.  She could ensure that everyone within a mile's radius could hear her voice as if she was right next to them, and she used it now, producing a high-pitched, full volume scream, right in my ears.  In Golem's ears.  Everyone's ears.



I joined Golem in doubling over, using my hands to try and ward off the sound.  It didn't help as much as it should have.  It was loud, deafening, and it was leaving Golem vulnerable as Crimson closed the distance.  He wasn't recovering fast enough.



Bugs flowed into Screamer's open mouth, much as they had with Alexandria.



I gave Tattletale the signal.  \emph{All out attack}.



This was it.  They'd been okay with a little bit of involvement on our part.  Tattletale had speculated they would.  There were only a few who were so regimented they would report it to Jack at the first opportunity.  Winter was among them, but she was largely in the dark, here.  Screamer wouldn't fill her in if it meant spoiling the fun.



In truth, the only ones who wouldn't let us get away with this were Mannequin and King.  King was distinct enough for me to notice, and Tattletale was ninety-five percent sure Mannequin would need more time to set up.  This was an approach we could only use with this first skirmish.



But whoever we were up against, the moment they started losing, the moment we actually pulled an \emph{offensive}, the line was crossed.  This was an all or nothing.



Stinging bugs attacked Cherish, going for the eyes, nose and mouth.  Screamer choked.  Somewhere in the midst of it, they managed to give a signal.  It wouldn't be Screamer.  Cherish?  Creating an emotional push?



Winter made her way out from downstairs, hefting a grenade launcher.



I spelled out words for the camera: \emph{Need Reinforcements}.



``\emph{The other teams are getting harassed, can't close the distance.}''



I was going to spell out a response, get further details, but my focus shifted as Winter caught sight of Golem and Crimson and advanced.



Her dynamic with Crimson was one of \emph{synergy}.  She captured people so he could feed.  He was the front line so she could safely attack from range.  She slowed down opponents so he could advance.  He was immune to her munitions fire, in large part.



My bugs swarmed her, but she was already concentrating her power.  Smaller area, greater effect.  She still held the people in the building in the area, but my bugs were lasting only a fraction of the time.  Seconds.  I activated my flight pack and approached.



Golem finished creating his hand, but there was a limit to what he could do with it.  It stood there, tall and useless.



No, his focus was on escape.  He thrust both hands into two different panels, slightly out of sync.  One hand was created, almost twice the usual size, and another was simultaneously created from the palm of that same hand, a fraction smaller.



Campanile's idea.



Both hands thrust out at virtually the same speed that Golem might have stuck his own hand out into the air, but that speed was compounded by the fact that both hands thrust out in unison.  Golem set one foot down and vaulted himself up and out to land on the adjacent building, one story up.  He spun around as he landed.



Crimson gave chase, crossing the rooftop with heavy footsteps.



Golem jabbed out with one hand as Crimson bent his knees to leap.  The hand that appeared jabbed at the underside of one foot, lifting it.



It was the sort of trick that would only work once on an enemy.  The next time, the enemy would adjust, or jump off one foot.  Here, it caused Crimson to stumble.  He missed his mark, the jump failing, and he nearly ran straight off the end of the rooftop.  He struck out with his sword, slamming it into the brick of the building face opposite him.



Winter raised her grenade launcher and fired.  Golem managed to vault himself away as he had earlier, a shallow movement that was forceful enough to nearly launch him off the building.  He rolled on landing as the grenade disintegrated a corner of the building.



These two were warriors.  Crimson was a mainstay of King's era, when he'd ruled the Nine as more of a brute squad, not dissimilar to the Teeth back in Brockton Bay.  I had trouble marking why Winter had been recruited, but it likely had more to do with how she was \emph{off} the battlefield, her predilections for torturing people she'd caught in her torpor.



I reached the edge of the battlefield.  My bugs streamed forth, a silk cord trailing between and behind them.  The silk streamed out from the spinning spool at my belt.  Hundreds of feet of material, and it extended out towards Winter.



It was only a matter of feet from her when she jumped, startled, leaping to one side.  I missed, and my bugs were dying in a matter of seconds.  The cord went slack.



A moment later, she was looking around, confused.



\emph{Cherish, }I thought.\emph{  She alerted her, a burst of alarm}.



It didn't matter.  My swarm approached from the other direction, finding and picking up the dropped cord.  Moving them within Winter's effect range was a matter of relay, handing off to fresh bugs as they died.  Slow but steady progress.



The moment the silk thread was around Winter's neck, I dropped down to the edge of the rooftop, and used the mechanical arms on my flight pack to reel in the cord.



Darwin's spider silk.  Stronger than kevlar, a narrow cord of it made for a thin, almost unbreakable cord.  The noose cut into her neck, and my arms and legs provided leverage to keep me still as the combined efforts of the mechanical arms provided the strength.



When she reached the base of the building I stood on, she was lifted off the ground.  I shifted my position to improve my leverage and waited, hiding.



I could barely tell in the midst of her power, but I sensed her raising her arm.  Raising the grenade launcher.



Nets of spider silk peeled away from the gray-white portions of my costume as my bugs pulled them free.  I drew it out, connected the narrow sheets with knots of more silk.



It moved into place just in time to catch the projectile out of the air.



Golem managed to find a moment to use his power.  A hand of stone struck the grenade launcher from Winter's hands.



He was holding his own against Crimson, who was adapting.  Golem thrust one hand into his armor to create a hand beneath Crimson, and the villain leaped closer, forcing Golem to vault himself away and maintain a safe distance.  The sword swipe that followed after Golem's retreat passed within a foot of the hero.



Wanton, surrounding Golem, advanced on Crimson, and Golem tossed out a bag.



Wanton took hold of the bag and emptied it of its contents.  Razor blades, caltrops, hooks and my threads joined the miniature maelstrom, and Crimson was slowly bound.  He tore some free, but it found its way into his flesh again a moment later.



Then Golem slid his right hand into his armor.  Crimson leaped in anticipation of an imminent attack, landed, and then glanced back at the point where he'd come.



Nothing.



Golem continued sliding his hand into his armor, slow, inexorable.



Crimson charged, and Golem backed away, using his free hand to erect barriers.  Wanton ran defense, and Crimson stumbled.



A rumble marked Golem's \emph{real} direction of attack.  A \emph{second} hand, down on the street below, gripping the large, six-story tower he'd created earlier in the fight, pulling it down.



It toppled on top of the building that Winter and Crimson had emerged from.



Toppled towards Screamer and Cherish.



In that same moment, Chuckles made an appearance.  He moved so fast it was almost as though he teleported, appearing beside the two girls.  My bugs barely had time to make contact and try to get a sense of him before he was moving again, holding the two villains this time.



They jerked to a stop.  I felt a fraction of the same confusion Chuckles no doubt did.  I sensed his arms, extended to ridiculous lengths.  He realized they were caught, bound to the computers.  Too entangled to take along.



And then he was gone, out of the building as the hand struck home.  Two floors crushed, the two villains crushed with them.



Tecton had provided the calculations on what the building could withstand, I'd provided the general data and information on where the hostages were.  The damage was controlled, the hand crashing a specific, certain distance into the building before coming to a halt.



``\emph{Bitch and Foil tried to intercept Chuckles just now as he left the city.  He escaped, but Foil hit him with one shot,}'' Tattletale said.



``Right,'' I said, even as I swore to myself.  \emph{Shit, shit shit shit}.



Far too soon for Jack to get a report on the fact that we'd helped.



``\emph{Chuckles can't talk},'' Tattletale said.  ``\emph{He laughs, but he can't talk.}''



I shook my head.  Couldn't worry about that right now.



Crimson was only staring at the wreckage.  He mumbled something around a bloated tongue.



\emph{Does he think Winter's still in there}?



Then Crimson charged Golem once again.



Golem had both hands free, and he used the same double-hand technique to strike again.  A second hand, sprouting from the first, which emerged from the rooftop in turn.  The hands caught Crimson in the side of the leg, slamming into the knee, using the curve of the thumb to catch the leg and limit the range of movement.



Strong as Crimson was, he was still bound by physics and general physical limitations.  Being struck in the knees \emph{hurt}, and he still needed to maintain a sense of balance.  He toppled.



Another double-hand strike, and Golem caught Crimson in the groin as he landed on his hands and feet, shoved him off to the right.



Two more strikes, this time not doubled-up, catching Crimson in the left arm and left leg, respectively, keeping him off-balance.



The key was to deny leverage.



An arm looped over one leg and one arm, binding them to the rooftop.  Crimson tore free with little effort, but the act meant he shifted his weight to one side.  Golem capitalized on it with another double-speed strike to his side, pushing in the same direction the blood-gorged killer was already moving.  That was followed in turn by one larger hand, moving slower, to scoop Crimson up and tip him off the edge of the rooftop.



Crimson fell.  Not a fatal fall, but it would hurt some.



A gauntlet of concrete seized the large hand Golem had just created and tore it free of the rooftop, then let it roll free to fall right on top of Crimson.



With the villain in an alley, the ensuing takedown was just as brutal and tenacious as before, with the added advantage that there were walls on either side to strike from.  Hands struck out, and they remained there.  As the villain was denied any footing, any balance, the hands around him increased in number, folding around him, sliding into gaps.



It was a parallel to Kaiser's pyramid of blades technique, that he'd used to try to entrap Lung.  I'd passed it on to Golem, but I hadn't told him the source.  I got the sense he wouldn't appreciate it.



I turned my attention to Winter, who dangled beneath me.  She'd gone silent and still.  I continued to wait, but I raised one hand to my ear.  ``Tattletale?  All four are down.''



I could speak.  A benefit to Screamer being dead.



``\emph{Good.  Too soon to tell if Jack's got wind of what you're doing}.  \emph{But if Chuckles passes on word, or if there's a Nice Guy in the area\ldots}''



``I wouldn't think he'd use the same guy twice in a row.''



``\emph{No,}'' Tattletale agreed.  ``\emph{The numbers fit, makes sense he'd start with four with a fifth as backup, considering how he can scale up the numbers in successive attacks.  Still-}''



``There was no graceful way to do it with Cherish there, and I couldn't \emph{not} help.  Golem was incapacitated.''



``\emph{I'll let Chevalier know what happened?}'' she made it a question.



I sighed.  \emph{No point in keeping secrets amongst ourselves.}



``Do.  And send Foil here,'' I said.  ``She can punch a few holes in Crimson while he's trapped.''



``\emph{Will do.''}



I waited another minute as Winter dangled from the thread, then cut her free.  Her body crumpled in a heap at the base of the building.  I made my way over to Golem and Wanton, where Wanton was still in his breaker form.



This was the warm-up, for the Nine, for us.  Four down, two hundred and seventy-some to go.  Jack had a little information on us, no doubt.



I didn't dare hope it would \emph{stay} this simple.  We still needed to find a way to narrow down Jack's location, killing him.  He already had an advantage, wearing us down, costing us time, and he surely had \emph{some} intel on us.



I could only hope that intel didn't include the fact that Golem had help.



``\emph{Chevalier here.  We have reports that they're showing themselves for the next locations}.\emph{``}



I met Golem's eyes.



``Locations, \emph{plural}?''  Golem asked.



``They want you to choose,'' I answered him, as the realization dawned on me.



He stared at me, lost.  He was heaving for breath, his hands shaking visibly, even with gauntlets on.



``Go with the Chicago teams.  I'll take the Undersiders and Brockton Bay Wards to the other location,'' I said.



He nodded, pressing one hand to his ear as he started making his way to the ground.  I watched him for a moment, then took off.



This was a statement, I suspected.  I could guess what that statement was.  Jack fully intended to double down on the challenge each time we came out ahead.





