





``Hey, Weaver?''



I had to twist around to look at Crucible.  We were in the hallway just outside a set of elevators, windows on one side, doors at either end of the hallway leading into offices.  This was something of a waiting game, as Tecton and Revel got their teams into position to support Golem.



Through countless stakeouts, I'd found a routine.  Cheating on the `can't do anything but sit there' rule and reading while my bugs saw to everything else was a part of that routine.  I was nestled in between two pillars that sat between clusters of windows, my back against one, one knee propped up, a file in my lap.  My cliff notes on the various members of the Nine.



``I wanted to say thanks,'' Crucible said, ``Appreciate the invite.  Hundreds of superpowered lunatics, some of the scariest guys around, and that's not even the scariest part of all of this!  But Chevalier's all, `\emph{Weaver} specifically asked if you'd help.'  How the hell am I supposed to say no to him?''



``You just say no,'' Clockblocker said, before I could respond.  ``You're team leader, I'd even argue it's your \emph{job }to say no when the situation calls for it.  More than leading the team, more than strategy or handling double the paperwork or attending the meetings.  You decide what jobs are out of your team's depth and you tell the bosses to go fuck themselves, in the politest terms possible.''



``It's \emph{Chevalier}.  Important guy.''



``And when we asked you if you were okay with me taking command, that was your opportunity to say no.  His rank doesn't matter.  He'd probably respect you \emph{more} if you told him your team wasn't prepared and then stuck to your guns.''



``\emph{You} didn't tell anyone to go fuck themselves,'' Crucible said.



``No.  And I agreed to help out with this because this is \emph{important}.  My old teammates have been preparing for this in their own time, and-''



``-And you've got a thing for Weaver,'' the Ward I hadn't yet met said.  It was a girl, flanked by five shadowy silhouettes of herself, who were sitting around her on the other side of the hallway.  I'd read up on her, and I knew her as Toggle.  The `baby' of the team, it seemed, at fourteen.  She held what looked like a mace, but it, along with the layered body armor she wore, had circles of light glowing in shifting colors.



There was a long, awkward silence.  I glanced at Clockblocker, but he appeared unfazed.  Not that I could really tell.  His armor still had animated clock faces digitally displayed on the open spaces, and there was one in the middle of his face.  Was the varying speed and position of the hands supposed to indicate something, or was I reading too much into it?



``That was a joke,'' Toggle said.



``I'm not dignifying it with a response,'' Clockblocker said.



``Clocksie's sweet on Weaver,'' Imp said.  ``Aww.''



``\emph{Clocksie},'' Clockblocker said, deadpan, ``Has been the target of a lot of criticism, because he was in charge of the Wards at the time a lot of stuff went down.  Some dingbats online speculated that I had a thing for Weaver, and it took off.  The people online like to find stuff that fills in blanks, and there were a hell of a lot of blanks around the whole thing with Weaver defecting, and our pseudo-truce with the Undersiders.''



``They latched onto the idea,'' I said.



``Yep.''



``Sorry,'' I told him.



``Not your fault, not exactly.  The city's pretty peaceful, pretty safe, and nobody even hints about why, but people know.  My bosses know why, and that means my career might never recover.  The only thing keeping things remotely interesting is the challenge of trying to get to any new bad guys before the Undersiders do, to enforce real justice instead of vigilante scare tactics-''



``We're awesomely good at the scare tactics though,'' Imp cut in.



Clockblocker ignored her.  ``-Except we barely even get to do \emph{that}, because Tattletale's always a few steps ahead.  Then, to top it all off, I hear about the Weaver-Clockblocker thing \emph{every single day}, to the point that it's \emph{sad}.  Salt in a wound.''



Silence lingered.



``Jesus, Clock,'' Vista said, after that.  ``Pent up much?''



``Fuck, you're right.  I'm stressed, ignore me,'' Clockblocker said.  ``Like Crucible said, it's a lot to manage.  Sorry.''



``I just wanted to make a funny,'' Toggle said.



``Don't worry.  Clockblocker used to be the funny one,'' Vista said.  ``Now he's the asshole grown up that tears the funny kid to shreds.''



Clockblocker didn't respond to that.  Instead, he shifted the device he'd been wearing on his back against the wall and sat down between the elevators.



Waiting on my lonesome was easier.



My bugs crawled all around the exterior of our target.  The buildings in this town were smallish, the tallest being five stories, and this contingent of the Nine had chosen it as their destination.



Not a single gap.  They'd barely had any time, but they had hermetically sealed the structure, containing themselves and every single resident within.  The windows and doors had been sprayed with something red that trickled out of cracks only to harden.  My bugs explored cracks in the foundation, and found that same vaguely tacky, amber-like barrier blocking the openings where they should have been able to enter the building.



Doors, windows, cracks, vents, all protected.



I could estimate seven apartments per floor.  One on the ground floor, for the building manager.  Assuming they weren't bachelor apartments, that suggested fifty-five to sixty people in total, trapped within, along with hostages and an unknown number and composition of the Nine.



``I have to ask,'' I said, not looking in Clockblocker's direction, ``This end of the world thing.  The way you talk about the future, life beyond this supposed apocalypse event.  Can you do that because you're \emph{optimistic,  }or because you don't think it'll happen?''



``I do it because I have to.  You can't stay sane, thinking it's all going to end soon.  There has to be something beyond it.  If you get to that point and then we figure out a way to resolve it, then what happens after that?  You need a real life.''



``If you get to that point and you've plotted out the rest of your life, and we \emph{lose}, then aren't you going to be devastated?'' I asked.



``I'm good at handling devastation,'' Clockblocker said.  ``Don't worry about me.''



I shrugged.



``\emph{I} can't really believe it,'' Crucible said.  ``World ending situation?''



``Oh, I believe it,'' Clockblocker said.  ``The crazy powers we get?  One of them's bound to break something somehow.''



``The wrong power in the wrong hands,'' Kid Win said.  He'd reconfigured the outside of his suit so the armored upper body folded down into a pair of gauntlets, allowing him to walk forward like a gorilla, the two halves acting as massive fingerless gauntlets.  It wasn't pretty, and it left his head and upper body more exposed, but it let him maneuver inside.  He seemed to muse a second, then agreed, ``Yeah.''



\emph{Interesting to see the divide}, I thought.  The veteran members vs. the newer ones.



``See, I don't think it's the wrong power in the wrong hands,'' Clockblocker said.  ``I think it's a joke.  Humanity destroys itself, and all these powers, they just open the door to let it happen.  It's not going to be some villain overlord or even a monster like Jack who does it.   I'm more liable to believe the world ends because of some deluded, fat, pimply faced punk kid that lives off pizza and mountain dew.  There's no damn \emph{point} to it, but sometimes I look at the idiots, the selfish assholes and the maniacs that fill this world and I think that's all we deserve.''



``I like your line of thinking,'' Imp said.  ``The world gets destroyed by some loser who jacks off twelve times a day to the freakiest, nastiest parahumans.''



``Thank you,'' Clockblocker said.  ``For so eloquently demonstrating what I was saying about us deserving it.''



``No problemo,'' Imp said.



``That doesn't exist, does it?''  Toggle asked.  ``Case fifty-three porn?''



``Everything exists,'' Kid Win said.



``Um, it just hit me.  When you were saying we deserve it, were you talking about pimple-face the world destroying freak-fetishist or were you talking about me?''



I shut my eyes and tuned out the conversation.  It was good that they were talking, staying calm, more or less getting along.



Grue and Rachel arrived from the stairwell.



``Anything?'' Imp asked.



``No,'' Grue said.



``The Red Hands leave already?'' I asked.



``Yeah,'' Grue said.  ``Listen, about all that, it's-''



I raised my hand to stop him.  ``Not important.  Not a big deal.  I was only going to ask if maybe Crucible or Toggle could be taken along.  It's a way out, now that things are getting heavier.''



``No.  It's fine, I'll stay,'' Crucible said.



``Ditto.''



I nodded, then looked at Grue, shrugging.  ``That's all.''



``We're okay?''



``Copacetic,'' I said, turning my attention back to the file.  \emph{Skinslip}.



I reread the page four times before I was sufficiently distracted and able to register what I was reading.



Rachel directed her dogs to watch the stairwell, then crossed to the middle of the hallway to me.  She sat with her back to the same pillar I had my back to, her shoulder pressing against mine, squishing me a little bit further into the crevice I'd settled in.  Not uncomfortable.  Or it was, but the body contact was comforting enough that it didn't bother me.  It was reassuring without being in my face or distracting me from my study of the folder.



All stuff I'd read backwards and forwards, but I couldn't focus on a book, and refreshers could only help.



I turned the page.  Night Hag.



``How's life on the dark side?'' Kid Win asked.



I turned my head.  He was talking to Foil, who sat at the furthest point from the stairwell.



``More wholesome than you'd think,'' Foil said.  ``Playing into every stereotype ever, moving in before we'd even been on a date, but it's nice.''



``Nice?'' Clockblocker said.  ``Not what I expected.  Not that I'm not happy for you, but-''



She shifted position, resting her head on Parian's shoulder.  ``It's\ldots free.  Pleasant.  The times between the fights with the brain-shatteringly terrifying god-monsters, anyways.  Cooking breakfast, having breakfast cooked for you, going on walks with the dogs, maybe a bit of bodyguard duty while Parian handles a meeting, whatev, picnic for lunch, patrol the territory, do stuff for my University course, whoever didn't cook breakfast makes dinner\ldots''



``They're like a newlywed couple!  It's so sweet,'' Imp said.  ``Of course, they're skipping the-''



``No,'' Foil said.  ``We don't need to go into any detail about my personal life with Parian.''



``But I was just going to say-''



``No,'' Foil said again.



``-they've got crazy good interior design, what with Parian and all,'' Imp finished.  She made a smug little sound, like she was very pleased with herself.



Foil flicked a dart at Imp.  It sank into the wall just to the left of Imp's head.



Vista leaned back, smiling, ``This is the second time in four minutes where she's alluded to rude stuff.  Feeling lonely, Imp?''



``I'm offended!  Unfair accusations!''



``Now I'm going to start wondering what someone with pseudo-invisibility powers gets up to in her alone time,'' Kid Win said.



``She's gone there,'' Grue said.  I looked at him, and saw he was glancing my way.



``Lies and slander!''



``Wait,'' Clockblocker said.  ``I thought I heard something at some point about you being her\ldots''



He trailed off.



``Hm?'' Grue asked.



``Train of thought derailed.  What were we talking about?''



It was a puzzling change in the ambient tone, and I almost gave the word for people to switch to high alert.



I was distracted by the vibration of my phone.



A quick check and I verified that it was what we'd been waiting for.



Golem engaging. 3x Burnscar, 3x Shatterbird, 2x Winter, 1x Skinslip, 1x Psychosoma identified.



You're clear to go.



``We're moving,'' I said, hopping to my feet.



Just like that, the mood shifted.  Everyone was standing, picking up the equipment they'd put down.  The joking atmosphere was gone, the\ldots not \emph{peace}, but the stillness, it was broken.  Nerves were suddenly on edge, the opportunity to joke and comment gone.



``Scouting with the bugs didn't turn up anything,'' I said.  ``Place is sealed.  Vista, we'll be counting on you to give us an in.''



She nodded.



``We're going in blind.  We suspect there's at least two Mannequins, but that's it.  Mannequin specializes in indirect attacks.  Catching people off guard, while being durable and flexible enough that he can escape from any situation that doesn't go his way.  I hope the rest of you have read up on the other members of the Nine, past and present.''



There were nods all around.



``Parian, Foil, Kid Win, you're staying here.  Set up, keep an eye out and an ear out.''



``Will do,'' Parian said.  She was already inflating a stuffed scorpion.  Cloth bound around one of Foil's bolts to help form a tail.



``Grue,'' I said.  ``Hit the building, inside and out, but leave the inside clear.  With luck, we can shut off their communications.  With \emph{more} luck, you can get a bead on what powers we're dealing with.''



He nodded.



With that, we were down the stairs and out the front door.



A joint attack maximized the chaos and minimized the chance of reinforcements.  Golem was attacking the other location.  Ten members of the Nine there.  Ten here?



If so, that was a big step up from the last fight.  From four or five to \emph{twenty}.



Grue used his power, surrounding the area.  Slowly but surely, the area was consumed in darkness.  Not just Grue's power, but the fact that the massive cloud of darkness was blocking out the ambient light.  Though he kept the smoke out of the center of the area, it grew darker with every passing second.



I joined the Brockton Bay Wards as they switched on flashlights, both handheld and gun-mounted ones.  Each of us flicked on the smaller lights that were part of our masks or helmets.  The latter were feeble at best, but it was still \emph{light}.  Mine came from smaller lenses that sat around the larger ones that covered my eyes.  They filtered out as a faint blue.  The pattern and color would hopefully make me more identifiable.



``It's kind of dumb that we don't have those things,'' Imp commented.



``Perk of being a hero,'' Clockblocker said.  He handed her a spare flashlight.



I gave one to Rachel, but she didn't turn it on.  Instead, she slid the loop over her wrist, hopping onto her dog's back.



The walls of darkness that surrounded the structure connected at the very top, and we were plunged into the deep sort of darkness one might expect from being a thousand feet underground.  The headlamps and flashlights were the only real light, making it look almost as if the exposed pavement, sidewalk and the foot of the building were the only things that remained in the world.



Vista used her power as we got closer.  I could see a depression appearing in the wall, as if a giant, invisible finger were pressing into it.



A hole appeared, and a small explosion tore out through the space, opening the hole wider.  We staggered, and some of our smaller members were even thrown to the ground.



Pale mist cleared slowly as we got to our feet.  My bugs scanned the area, searching for threats who might have been alerted to our presence.



Nothing.  Apparently they didn't want to engage.  They were happy hunkering down, staying eerily quiet.



And the explosion\ldots there was a byproduct.  Or maybe it was the source.  A small glacier had formed around the hole, jagged, as if water had spewed forth and immediately frozen.



``The hell?''  Clockblocker muttered.



\emph{Good thing it wasn't Tecton knocking down the wall,} I thought.



Vista tried again, higher up, on the fourth story, off to the far side.



We were braced for the detonation this time.  I kept bugs close to get a sense of what was going on.  The moment there was a gap, the air rushed out, cold and wet, and was followed soon after by a crushing manifestation of a small iceberg.



It creaked, a long, drawn out sound, then cracked abruptly.  The iceberg came free, and the resulting gap was almost instantaneously filled by a \emph{third} detonation.  A chunk of ice the size of a large car dropped to the street and shattered into a million individual fragments.



\emph{Or maybe Tecton would be an asset here.  How the fuck do we break into this?}



``Has to be Mannequin,'' I said.  ``Or Sphere.  Used to specialize in closed systems.  It makes sense, on a level, but this isn't in Mannequin's usual repertoire.  Maybe they stole it from\ldots what was the name?  Toybox tinker, Gelid?  Glace, that's it.''



``A cloned tinker is the smallest threat,'' Clockblocker said.  ``Takes them time to build, and if you figure Jack didn't exactly save anything of his, and\ldots well, I don't even know how they replaced memories, but there's no way he's just going to pick up where he left off.''



``Mannequin in a different vein,'' I said.  ``Same psychosis, different direction taken?''



``Looks like, doesn't it?''



I frowned.



``We could wait for the ice to melt,'' Imp suggested.  ``Warm out.''



``Would take forever,'' Vista said.



``And it would only get replaced, probably,'' Clockblocker said.



``Go big?'' I suggested.  ``Whatever's producing the ice, there's got to be a limit in terms of materials.''



Vista nodded.



This time, rather than a depression, it was a line, running from one corner at the bottom of the building to the opposite corner on the top.



It took ten or fifteen seconds, and then the ice blasted out, barely visible with only our flashlights to illuminate it.



Nothing.  Ground to roof, the ice remained.



``I could do it again,'' Vista suggested.



``Faster to get Kid Win to just tear the outside of the building apart,'' Clockblocker said.  ``Not like they don't know we're here, now.''



``I'm thinking,'' I said.  ``You know that draft of cool air you feel when the automatic doors of a big-name store swing open?''



``Sure,'' Clockblocker said.



``It's designed like that, to use air pressure and air flow and whatever else to keep bugs and debris out.''



``Of \emph{course} you know that,'' Imp said.  ``Because of the bugs.''



``I looked into it when I started paying attention to places where there aren't a lot of bugs, to see why.  There's sonic countermeasures, and there's that.''



``Whatever,'' Imp said.  ``Still pretty random.''



``This is the \emph{same thing}, except it's weaponized.  Or made into a defense system, depending on how you want to look at it.  I'd bet most of the building is rigged with some crazy high pressure, as well as whatever devices he's got that are detonating on exposure to the outside.''



``Okay, with you so far,'' Clockblocker said.



``But where are they keeping the hostages?  Option one is that they've got them in some sealed area, like they stuck Cherish into, and all of the Nine members in the building are immune to that pressure and cold.  Multiple Mannequins, maybe a Siberian in a sealed case?''



``What's option two?'' Grue asked.



``The inside is safe.  Apartments or offices bordering on exterior walls would be pressurized, but the interior walls, all of the rooms of the building that \emph{aren't} rigged, they'd be safe, with hostages and the Nine inside.''



Clockblocker nodded.  ``Makes sense, but that's a lot of speculation.''



``Theory two is a lot easier to prove,'' I said.  ``We either need to go in through the top, and hope the roof isn't as protected-''



``-or access the interior without passing into exterior rooms,'' Vista said.



\emph{Shuffle could have done that}, I thought.  Had we sent the wrong teams to the wrong locations?  It had sounded like there was a hell of a lot of offensive power at the other location.



``I'll try,'' Vista said.  ``Hold on.''



This was a more refined use of her power.  She drew on the exterior of the building, and created a depression, but the goal this time wasn't to create a hole.  She extended the depression inward, but she fed enough of the surrounding material into it to keep the resulting walls intact.



It stopped, and she merged it into another wall.  I couldn't \emph{see} the wall, but I could sense it with my bugs.  To my eyes, it was a black void, a hole too deep for my bugs to reach.



She paused, then began opening an experimental hole in the far wall.  I pulled my bugs back to make it easier for her.



I could feel the warm air blow past my bugs.  I could \emph{smell} it using their senses.  An alien sensation, but I noted the scent of blood, the acrid chemical odor of the sealing materials.



``Way's open,'' Vista said.



``It's messy in there,'' I said.  ``Be prepared.  Sending bugs in now.  Grue?  Darkness.''



We waited as he pumped the building full of darkness.  My bugs made their way through, scanning the surroundings.



``Murder Rat,'' Grue said.  ``Three of her.  I can\ldots kind of sense what others are sensing around me, and there's a glimmer of something that might be a teleportation power.  I don't trust myself to use it without any ability to sense where I'm going.  Breeds\ldots And\ldots I can't even get a bead on this guy's powers.''



Was it?  I could sense figures moving throughout the darkness, but they were swift, and moved in unpredictable directions.  The elevator shaft's doors had been opened, and they climbed up and through with no difficulty.  There were countless people, hanging from the ceiling by chains, countless pieces of armor, as though Mannequin was trying to reinvent his own gear, and then on the penthouse level\ldots



A man, easily eight feet tall, muscular and broad-shouldered, sitting at a computer chair with one foot propped up on a desk.  His chest was bare, his pants no doubt a normal size, but rendered skintight by his sheer mass, left unzipped.  He was watching something violent on a laptop as he sat there.  The hostages who weren't strung up with chains were in the room, cowering behind him as a full cluster.  In the midst of them, there was something that looked like a coffin.



``Try using his power?''



``Not sure I want to,'' Grue said, ``But okay.  Um.''



I felt my powers dim, my range swiftly dropping.  Others stepped away from him in surprise.



``Stop,'' I said.



He did.  My powers started to return.



``That's one.  Jesus, that's a rush.  The other\ldots I think it's the sort of power you need the built-in second sense to grasp.''



``That has to be Hatchet Face.  I guess you can use his power nullification,'' I said, ``That's something, if we hit a pinch.  I just don't understand this other power.  Bonesaw's work?  A hybrid?''



Grue nodded.  ``Possible.''



I frowned.  ``Not sure how to do this.  If we entered through the top floor, we could access the hostages right away, defeat Hatchet Face.''



``Sounds good,'' Clockblocker said.



``Except\ldots what do the rest do?'' I asked.  ``Some signal goes off, or they realize something's up\ldots they're not fighting types, not exactly.  They're assassins, indirect attackers.  They wouldn't just converge on us.  I don't know how they'd react, and it's not the kind of situation where I can say that in a \emph{good} way.''



``We need to make a call soon,'' Grue said.  ``You said the other team is already attacking?''



``I thought this would be \emph{simpler},'' I said.  ``Let's go in the ground floor.  Clear each floor, block off escape routes, so they can't just exit the building and go wreak mayhem elsewhere, or notify Jack.  They can fall back to the main room where Hatchet Face is waiting, and-''



``And then we've got a hell of a fight on our hands,'' Grue said.  ``Against enemies with hostages.''



``Cornered rats with hostages,'' Vista said.  The little of her face I could see in the flashlight-illuminated gloom was somber.



``Ground floor,'' I said.  ``If nothing else, it buys us time to think of something before we reach a crisis point.  The alternative\ldots I don't like the idea that so many of these guys could escape.  They've bottled themselves up nicely.  Stay on your guard.''



``Are you staying outside?'' Clockblocker asked me.



I shook my head.  ``Need to maintain communications against this team, and I don't like how long it would take to communicate using my bugs, or the chance you could get cut off.  I'll come with, help watch your backs.''



There were nods all around.



``Go,'' I said, before touching my earbud.  ``Tattletale.''



There was a pause.



``\emph{Weaver}.  Kind of busy watching over the other team.  Sup?''



``Entering the fray.  Looks like Mannequins, Murder Rats, Breeds and one Hatchet Face hybrid.''



``\emph{Got it}.  \emph{G'luck}.''



Rachel had kept the dogs at a smaller size so they could patrol the building we'd been hiding out in.  It meant they were big, but not so big that they filled the entire hallway.  They passed through the corridor Vista had made without trouble.



We filed in, shoulder to shoulder, and I did what I could to track the various villains in the building.  Grue dissipated the darkness as we got close enough to the respective areas to shine our flashlights on the objects in question.



Ominous, being in the midst of this building, almost like being in a submarine.  There was an incredible, devastating pressure all around us.  A leak meant a possible terminal end to all of us.  The darkness was oppressive, and every surface was covered in the red sealant, scabrous, hard, removing the human touch from everything around us.



I was so caught up in it that I nearly missed it.  A figure in the ducts.



``There,'' I said, keeping my voice low.  I pointed.



Our side turned to look.



\emph{Mannequin, }I thought.  I immediately switched mental gears.  Who to protect, what to do tactically.



I hit the briefest stumbling block when the recollection of what Clockblocker had been talking about crossed my mind.  \emph{Why does he remember his suit?}



The same outfit, with alterations.  The all-concealing, all-protecting shell surrounding his body, even the joints.



Bastard lunged for him, jaws snapping shut, but the Mannequin cartwheeled back and away.



Vista fired her gun, sending a single green spark zipping ahead.  Mannequin swayed to one side, bending his body at impossible angles to avoid the shot.  The bullet hit the wall, then briefly flared, disintegrating a scab-covered vending machine.



Lines exploded forward from Clockblocker's hands, one from each finger, and the Mannequin staggered back.  The narrow cables flew past him, glanced off his armor to ricochet into the surrounding area, and one or two even managed to wind around his arm or leg.



Clockblocker used his power, freezing the Mannequin in place.



``Vista,'' he said, ``Another shot!''



She still had her gun leveled at Mannequin.  She aimed-



And the Mannequin let a blade spring from his palm.  It punched through the wall at the very edge of our tunnel.



Ice exploded into the interior of the hallway, consuming the Mannequin entirely.



Vista dropped her gun.



``No escape route,'' Crucible said.



``Can't shoot without putting us at risk,'' Vista said.  ``I can make another exit, but it's going to take a minute.''



``Not a focus,'' I said.  ``Upstairs first.  Hostages first.  We'll cross that bridge after.''



We had to walk around in a semicircle before we found ourselves by the elevators and stairwells of the lobby.  The stairwell was framed by two bodies, hung by their feet.  No wounds were visible.



I felt with my bugs, and I could sense warmth from them.  Still alive.



\emph{Breed}.



What were we even supposed to do with his victims?



For the second time in as many minutes, I found myself saying, ``We deal with them after.''



We entered the stairwell.  I was aware of a Murder Rat popping in on the ground floor, crawling on hands and feet that each had excessively long blades on the ends.  She moved faster than she should have been able to, considering her means of locomotion, but she had an exceedingly strong, flexible body.  Enhanced senses, too, with her conical nose close to the ground, long greasy hair brushing against the surface.  I almost turned back to deal with her, but she was already gone, moving faster than my bugs could.



\emph{Claustrophobic}.  I was acutely aware of the dimensions of the space, the fact that only a fraction of the building could actually hold \emph{people}.  Of that portion of the building interior, the elevator shafts took up an awful lot of space.



\emph{Their} territory, really.



The stairs hadn't received as much of the `scab' treatment, but they were still treacherous ground.  The stairs blocked our view of what was above or below us.  I was careful to check for threats every step of the way, watching doors, sweeping over surfaces, all too aware that Mannequin had evaded my bugs before.



Had this one somehow retained the lessons the original had learned?  I could use thread to cover more ground, spread out my bugs.



An air vent at the very top floor was punched free of the wall.  My bugs could sense the long claws, the conical nose.  They started chewing on her, devouring and biting, but her skin was tough, as though most of it was scar tissue.  I could feel the hot air as she rapidly inhaled and exhaled.



``Murder Rat, she's on the top-''



She pushed herself free of the vent, lunging, drawing her claws together as if she were diving into water from a height.  Her narrow, emaciated body slipped right between the railings of the ascending and descending stairs.



``Incoming!'' I shouted.  I pushed the others back as I could reach them.  The only ones in reach were Rachel and Crucible.



She reached the stairwell just above us and kicked off it, changing her orientation and the trajectory of her dive.  She slammed into the largest, most obvious target -Grue- all of her claw-tips drawn together into one long spike.



He was thrown against the walls and the stairs, and his tumble down the stairs just below him drove him into Toggle and Vista, who nearly fell down the stairs along with him.



Murder Rat was still on top of him, shifting the movements of her limbs to remain more or less upright as she perched on his body.  Her head cocked quizzically.  The blades hadn't penetrated.



She lashed out, striking, only her target was exposed skin, this time.  Vista's face, Crucible's jaw.  Bastard's shoulder.



And then she kicked the wall, drawing her shoulders together as she slid between Clockblocker's legs, her nose pointed at the gap in the railing.



Clockblocker shifted his foot to make contact with the long blades at her toes, touching her, and froze her in place.



``My face,'' Vista whispered.



``Put pressure on it,'' Crucible said.  His own face was bleeding badly, but he didn't even seem to notice.



And, more troubling, the wound was smoking.  Murder Rat's power.



I turned my attention to Grue.  ``Are you hurt?''



``No.  I\ldots shit, how did that not break a rib?''



I shook my head.  \emph{Still using the costume I made, and it saved your life.}



He accepted my help in standing.  I turned my attention to the Brockton Bay Wards, but there were too many people crowded there for me to jump in and help.  I focused on the other threats.



I could sense the others swarming around us, on stairs above and below.  I drew out lines of silk to stop them from using the same approach this Murder Rat had managed.



For extra measure, I tied thread around the frozen Murder Rat's throat, tying it to the railing.



She was a composite of two `kitchen sink' capes.  Mouse Protector and Ravager.  Two primary powers that had blended into the one, a dozen other minor powers.  Flexibility, a bizarre kind of enhanced strength, reflexes and agility that had peaks and valleys, and skin as tough as leather.



``Pinch it shut, tape it,'' Clockblocker was saying.  ``We spray it to keep it closed.  Smells awful.''



``I kind of like the smell,'' Vista said, her words muffled by the hand Crucible was pressing to her face.  ``Hey, this'll be a badass scar, huh?''



``Quiet,'' Clockblocker said.



I could hear another Murder Rat on the stairs below us.  She let her claw drag on the wall, and the metal on concrete made a sound like five nails on a chalkboard.   Loud, slowly increasing in volume as she approached us.



I set my bugs on her.  She persisted, simply enduring what they were doing to her.  I tried to go for the tiny eyes that were nearly buried behind her altered face and brow, but she shut them, relying on touch and smell to move.  I started to pack bugs around her nose and mouth, and found that slowed her just a fraction.



But the noise continued.  I could see the effect it was having on the others.



A rattling noise from above, joined by another nails-on-blackboard screech.  A Mannequin, using the blades he'd extended from his forearms to scrape the wall and hit the individual bars that held the railing up at chest level, the same bars that the Murder Rat had tried to slip between to make her escape.



``It burns,'' Vista said.  Her fingers raised to the mark that ran from the side of her chin to her cheekbone.



``The meds?'' Clockblocker asked.



``The smoke.  Stinging my eyes, and feels like it's \emph{fizzing}.  I read the file, this is her power, right?  It's what she does?''



``It's going to take a long time to heal,'' Clockblocker said.  ``Pretty much guarantees a scar.  But we stopped the bleeding, which is better than most get.''



The dog growled as another Murder Rat joined the fray, her clawed feet clicking against the steps as she made her descent, the screeches of her claws against the concrete joining what was quickly becoming a cacophony.  The blades at the fingertips of her other hand struck the bars of the railing, which set them to ringing.



Then, from the first and fourth floors, I could sense Breed's minions make their approach.  In the midst of the banging and screeching, their hissing was almost impossible to make out.



One more Mannequin hung back, letting the little bastards climb on him.  They were smallish.  Smaller than the ones in Killington had been.



I shifted my weight, ready for one of them to make an attack at any moment.  Indirect attacks, surprise attacks, all from directions that were hard to anticipate.



``Three Mannequins and a Rat above us,'' I said.  ``Two rats below us.  Lots of Breed's bastard parasites on both sides.''



``I could use my darkness, but it wouldn't help much,'' Grue said.



``They don't sense things like we do.  My bugs aren't going to do much either,'' I said.  ``Laying tripwires and trying to bind them here and there, but these aren't guys my bugs can sting.''



``So?'' Rachel asked.



``We die,'' Imp said, with an odd cheerfulness.  ``Horribly, gruesomely.  They'll break or sever our arms and legs and cap them with Mannequin's stuff so we don't bleed out, and then they'll let Breed's bugs devour us from the inside out.''



``Not helping, Imp,'' Grue said.



``I'm only saying what we already know.  Kind of counterproductive, morale-wise, to have us read all the dossiers on these bastards.''



``Yeah.  Just a little,'' Crucible agreed.



``Why are we waiting here?'' Rachel asked, her voice a little too loud.  ``Why don't we just fucking attack them?''



I didn't have a good rebuttal to that.



No, that wasn't right.  I had a dozen rebuttals.  That these guys would take any offensive action on our part as an excuse to slip past us and murder our more vulnerable members.



But I didn't have a better strategy.  Not one I was eager to use so prematurely.



``Attack,'' I said.  ``\emph{Now}.''



Rachel whistled, a long sharp sound that cut through the various noises the Nine's members had created.  There was only silence as the whistle echoed through the stairwell.



She snapped her fingers and pointed up the stairs, snapped again and pointed down.



The two dogs charged in the alternate direction.



``Wards, go \emph{up}.  Grue, Imp, Rachel, help cover the rear,'' I gave the orders.  ``Watch your backs!''



We split into two groups, the Wards leading the charge, while the Undersiders covered the flanks.  I remained in the center, my knife drawn.



A Murder Rat tried to jump down through the gap, as the first had, but got tangled in the threads I'd woven.  She began severing them, one by one, but too slow to slip through.  Vista shot her.



With her death scream, the others shifted tactics, abandoning the offense.  Mannequins advanced to take over the assault.



Another got caught in the threads, but blades sprung out all over his body, the individual components rotating, and the threads were cut.  He dropped down.



Crucible caught him.  A forcefield bubble surrounded the figure, pale blue, then flared a brilliant orange-white.



Mannequin would be fireproof, though.  Even an extreme heat like Crucible could create wouldn't have an effect.  Still, it meant one was contained.



Yet as soon as we captured one, another slipped the net.  The Murder Rat Clockblocker had frozen animated again, slipping through the railing, only to find herself hanging by her throat, a silk cord binding her.  My bugs could sense blood trickling, but the movement suggested her neck hadn't snapped.



Two ways she'd escape.  The first was obvious, cutting the cord.



The second?



``Vista, Crucible!'' I hollered their names.



They whipped around to face me, saw me holding my knife, ready to drive it forward.



The smoke on Vista's face flared, blossoming like a smoke grenade that had just gone off, and Murder Rat materialized, one claw already poised with the points facing upward, ready to drive upward into Vista's unprotected jawline.



I'd seen her gesture as she hung on the rope, in preparation for her materialization.  I had to lunge forward, striking the stairs with the boniest parts of my shins to catch the villain's wrist with my free hand, pulling her off-balance.



She rolled with it, almost doing a backflip as she threw one leg back to drive a point towards Imp's scalp.  Grue caught Murder Rat's leg, and between us, we held her.  I punched the blade into her throat.



Grue heaved her over the railing.  He covered our retreat with darkness, then lunged ahead of the group.  Murder Rat's powers, it seemed.



Reckless, not like him, but he joined the front lines, where Bastard was giving two Mannequins a hard time.



Clockblocker threw out lines of silk, then froze them.  The dog lunged, and the Mannequins were sandwiched between the dog and the silk.



Blood spurted at the dog's shoulder where the lines had made contact.  One Mannequin lost an arm, but they both managed to contort and angle themselves so they could slip over, under or between the threads.



Of course it wouldn't be \emph{easy}.  Fuck.



``Back!'' Rachel called out, before the dog decided to charge through the cables Clockblocker had used.  The dog retreated a pace.  Grue only hopped up, grabbing the railing, managed a grip, and then descended on them.  He grabbed one and flung it towards the wires.



It only contorted, arching its back like a high jumper to slip through a gap.  It got halfway before Bastard closed his jaws on his upper body.



Shit.  My bugs were so useless here.  I couldn't go after the Breeds until I knew which of the people in the building were them.  The original Breed had died when someone had hit a building with an incendiary missile, and the bugs had stopped appearing.  He wasn't altered in appearance.  For all respects, he was just an ordinary man.



Besides the whole `I create horrifying space bugs' thing.



The Mannequin that crawled with Breed's creations leaped down, only to get caught in more strands.  He started to cut his way free, but Vista opened fire.  Her shots glanced off his outer shell.



The \emph{creatures}, though, fell through the gaps.  More than a handful landed in our midst.



``I thought you said they don't go after people!''



``They don't!'' I said.  ``So long as there's other food sources available.''  I kicked at one as it advanced on my right foot.



``There are dozens of bodies here!''



\emph{Already infected}, I realized.  These parasites were seeking fresh hosts, ones not already occupied by anything.



I caught the ones I could with my own bugs, used thread to haul them free, but there were twenty, and their dozens of legs were sharp, capable of punching through flesh and clothing to maintain a grip.  Difficult to dislodge.



One had landed on my shoulder.  I tried to pull it free and failed, stabbed at the legs with my knife, only for it to fold them into its carapace.  It lashed at the lens of my mask with its spike-tipped tail.  It didn't penetrate, and rolled off my shoulder before I could get a hold on it.



Its legs extended, and it found a grip on my flight pack.  In an instant, it was racing up towards my head again.  It stopped twice, pausing for one second as it transitioned from my flight pack to my costume, then stopping again as it reached the area where the mask and body of my costume overlapped at my neck.  The needle points of its legs were pricking through the fabric of my costume, no doubt as it tried to find a way under.  I got a grip on its tail, but failed to dislodge it.  Too slick.



The others weren't faring a lot better.  Crucible shouted something incoherent as he used both hands to stop a softball sized creature from advancing on his mouth.  Its millipede-like limbs left bloody tracks in his skin as it made excruciating progress towards the orifice.



It was a critical distraction as we were dealing with highly mobile foes.  A Murder Rat leaped up to find a grip on the \emph{underside }of the stairs we were standing on, then vaulted herself to one side and up, slipping between the bars and into our midst.



Rachel whistled, hard, and the dog from downstairs came barreling through our group.  We were knocked aside, pushed to the ground by the dog's mass as it charged Murder Rat.  She leaped up, stepping on the dog's back, then jumped back down to the lower end of the flight of stairs.



The dog growled and turned around, preparing to charge through us again.



``Hold,'' Rachel said.  She had to pull off her jacket to access the trilobite-parasite bastard thing that was crawling on the small of her back, heading south.  Toggle struck it with her baton, and lights flared.



Imp stepped up just in front of Crucible, impaling the bug on his face with her own knife.



Progress, but we were still in the midst of a lot of dangerous enemies.  Elusive ones.  Of the six here, we'd only achieved two kills.



``\emph{Tattletale here}.''



``In an ugly spot,'' I said.



\emph{``Help's on the way}.''



``Help?''



``\emph{Eidolon.  We tried to keep things quiet, keep everything off the radar, but he caught on.  Legend's at the other site with Pretender.}''



``Turn them away!'' I hissed the words.



``Um, not about to turn away help,'' Imp said.  She was benefiting as Crucible created his superheated forcefield dome to burn away the Breed-parasites too dumb to walk around.



``Turn them away,'' I repeated myself.  ``All three.''



More of Breed's bugs were starting to make their way to us, from above and below.  One Murder Rat, one Mannequin, and the guy upstairs we still hadn't even interacted with.



With his fucked up coffin.



``\emph{I can't get in touch with them.  Not like their number is in the phone book}.''



``Contact Cauldron?''  I used my swarm to attack the Breed-bugs, but it was slow going.  Twenty bugs with strong mandibles could kill one, but it took a minute, maybe two, before they reached something resembling soft tissue.



``\emph{No go}.''



I could sense him, now, approaching the building cautiously.  He used a laser to pierce the roof.  Ice blossomed out to fill the gap, a glacier in summer.



I began drawing from the bugs outside, forming a swarm-clone.  Eidolon ignored it, firing again.  Multiple blasts, multiple creations of ice.  He swore under his breath.



Rachel's dog leaped over us to attack the Murder Rat.  She slipped to one side, and a wound at Toggle's shoulder began blossoming with smoke.



The Murder Rat appeared in our midst.  Clockblocker was quick enough to tag her this time.



It wasn't the most ideal maneuver.  Grue's stolen power disappeared in that same instant.  Bad timing – he was in the midst of fighting the Mannequins.  One had been taken out by Bastard, but another had joined the fray as it brought the bugs down.



Grue reached out for another power.  Mannequin's power wasn't useful, but the other-.



I felt my power fading, just as the swarm-decoy was gaining enough bulk.



I wasn't the only one.  Crucible's forcefield shorted out.  Clockblocker had been in the midst of reaching for Breed-bugs to lock down, and found himself only giving them easier access in climbing up his arms.



The Mannequin staggered back, tripping on the stairs.  Just a little less coordinated.



Still, it wasn't useful.  One dog was entirely disabled, crawling with countless Breed-parasites.  Only the fact that it clenched its jaw kept them from getting in its mouth, but its nose-



``Cancel it, Grue!'' I shouted.



He didn't.  Instead, he reached down to grab Mannequin by the throat.  He ascended the stairs three at a time, dragging two struggling Mannequins with him.



A bad situation was turning into a nightmare.  My radius shrank to a mere hundred feet, then fifty.



Twenty.



The bugs were crawling on us, Crucible wasn't the only one struggling to keep them from worming beneath his hands and into his mouth.



Then he was gone, the radius of his power nullification too small.  If the Hatchet Face upstairs was a hybrid, Grue's copy of his power was a fraction of a half of a power.



Still, he seemed to have Hatchet Face's strength and durability.



Our powers began to return, and with the threats of the other capes dealt with, we were free to focus on stopping them.



Clockblocker paused the most dangerous ones, closest to mouths, anuses and private parts, to ears and nostrils.  We backed away as he freed us of the worst of them, and Crucible barred the path with his superheated forcefield.



``I'm not\ldots I'm not useful,'' Toggle said.



``Different threats, you would be,'' Crucible said.  ``Fuck, this stings.''



``Medical treatment after,'' Clockblocker said.  ``One more to take down.''



We hurried up the stairs.  Two flights to the penthouse floor.



``\emph{Eidolon},'' my swarm-clone spoke.



``Weaver.''  He had created a kind of portal and was widening it.  It seemed slow, inefficient.



``\emph{Go home, Eidolon.  You aren't a help here.}''



``I'm to take orders from the one who murdered Alexandria?''



``\emph{Yes.  Leave.  You're more danger than help.}''



``I can end this.''



``\emph{So can I.  I will end this.  Your choice as to how.  Do I handle this situation myself, or do I have to kill you, then handle this myself?}''



There was only silence from him.  He stared at my swarm-clone.



``You \emph{dare} make that threat, after killing my comrade-in-arms?''



``\emph{I do.  If there's a trace of doubt in your mind that I could do it-}''



``Your bugs couldn't touch me.''



Inside the building, we were approaching the penthouse floor.



``\emph{Your power is dying.  It's obvious enough that people are speculating on it online, in the media.  How Eidolon isn't as strong as he was in the early days.  Why aren't you inside already?  Are you so sure that your power would stop me?}''



``I'm here to help.  That's all.  Attacking me now would be like the violation of the Endbringer Truce.''



``\emph{You're one of the biggest dangers, Eidolon.  Jack's supposed to be the catalyst for an event, a great catastrophe.  Are you honestly telling me that there's no danger here?  That you're absolutely certain that you don't have a weakness he could capitalize on?}''



Eidolon didn't speak.



``\emph{Don't tell me you don't.  That you aren't potentially powerful enough to end the world if it came down to it.  If he somehow opened that floodgate-}''



``It won't come to that.  I control my powers.''



``\emph{Or played a head-game with you?  Are you telling me your mind is a fortress}?  \emph{That you don't have that capacity for great evil inside you?}''



``I'm not evil.''



``\emph{You participated in business that people felt was so horrifying that they seceded from the Protectorate.  How many thousands died or suffered gruesome transformations because of the atrocities Cauldron committed?}''



Inside the building, we opened the door.  Grue was staring down the last member of this particular group of Nine.  Tall, muscular in the way that suggested he was in his physical prime, with a wild mop of dark hair.  He was masculine in a way that exaggerated the qualities to a fault, with an overly square jaw, massive hands, an almost Neanderthal brow.  It made him look like a bad guy from an old animated film about princesses.  As if echoing that sentiment, a word was tattooed across his chest.



\emph{Tyrant}.



I recognized the other half of the pair.  Hatchet Face and King together.



Untouchable.  King's power took any physical harm he suffered and transferred it among his pawns.  People he'd touched within the last twenty-four hours.  Hatchet Face's power meant we couldn't even use abilities to circumvent it.  Tyrant here had the enhanced strength each of the two had possessed, the enhanced durability.



``Are you saying you're blameless, little murderer?'' Eidolon asked, just above us.  ``That you don't have a potential for evil?''



``\emph{No},'' I answered.  The hybrid crossed the room, and I could feel my powers fading.  Grue's darkness dissipated around the building, and light streamed in through the red windows, casting a tint over everything.



I shifted my bugs outside the building.



``\emph{No, I know I have some ugliness inside me},'' I spoke through my swarm.  My swarm was dissipating, my focus and control over my bugs failing.  I had to maintain the formation.



``Then what qualifies you to be here when I can't?''



``\emph{Maybe arrogant of me to say so},'' I said.  The swarm was quieter as my fine control swiftly dissolved.  ``\emph{But I've recognized that ugliness, and I've got it harnessed.}''



I gave the signal, gesturing for emphasis.  Tyrant paused.  The swarms outside the building shifted in the same moment, uttering the word faintly.



\emph{Now}.



Outside the building, Foil fired, and she used the line I'd drawn out with my bugs for guidance.  Not perfect, not ungodly straight, but the thread I'd drawn out helped.



There was a concentrated explosion of ice at the edge of the penthouse as the shot punctured the wall, passed within a foot of Tyrant.



He advanced, and I stepped forward to meet him, my eyes on his.  My power was almost entirely gone.  Dampened to the point that it was just me and the bugs that crawled on me.  Every step he took reduced it another fraction.  Half a foot, then an inch away from my skin\ldots



Another bolt, between us, closer to Tyrant than to me.



And then an explosion that seemed to shake the entire building.  Everyone present was thrown to the ground.



Kid Win had blasted a hole in the side of the penthouse, firing what had to be every single weapon at the same time.  Ice was swelling from the open area in fits and starts.



But it was enough of an opening for Foil to get a clear shot.



She shot Tyrant, and the bolt pierced his brain.



He collapsed onto his hands and knees, then staggered, starting to rise.



Another bolt through the spine.



A third through the heart.



He collapsed onto his face.



Foil's bolts broke the rules.  Apparently his power didn't work on them.



I slowly climbed to my feet, then stared up through the closing hole in the building at Eidolon.



``Go home,'' I called out.



He was still, hovering there.  I didn't break eye contact as he floated closer to me, until he stood only a few feet away.



``Sit this one out, for all of our sakes.''



He broke eye contact first.  His eyes fell on Foil and Kid Win.



``Please,'' I said.



He didn't move, looking across the street at the others.



Then, as if the courtesy of the \emph{please} had given him the ability, he spoke.  His voice was quiet enough that I was probably the only one who could hear.



``I live for this,'' he said.  ``It's what I do.''



It was an admission of weakness, not a boast.



``I know,'' I answered him.  ``But it's not worth it.  Even here, that coffin up there that Mannequin made\ldots if it's hiding Jack, keeping people from sensing him until the end of this lunatic game he set up, then he could say something.  \emph{Do} something, and you could become everything you're trying to stop.''



No.  I'd said something that was off the mark.  I saw Eidolon hesitate, as if he was considering going ahead anyways.



``And you're all so safe?'' Eidolon asked me.  ``You're not such a danger, with the right trigger event, the right saying?  You couldn't murder a town full of innocents as readily as you murdered Alexandria?''



``The difference between you and me,'' I said, ``Is if I go off the rails, if I somehow become an agent of the apocalypse, I can be stopped.  I can be killed.''



He stared at me, the shadows of his eyes only barely visible behind the blue-green expanse of the concave mask he wore.  The shadow cast by his hood didn't help.



``There's a quarantine, Eidolon.  Everything we're bringing to the table here, everyone who's on the front lines, they've talked about this, they've agreed.  We're all willing to die if it comes down to it, for the sake of maintaining that quarantine, keeping the end of the world from coming to pass.''



He looked past me at the Undersiders and Brockton Bay Wards.



``I'm willing to die if I have to,'' he said, in his eerie chorus of a voice.  ``I've proven that enough times\ldots but it doesn't matter, does it?''



``There's no guarantee we could stop you before it was too late.''



``I see.''



He cast a glance over our assembled ranks, then took off.



I waited long moments before turning my attention to the crowd at the far end of the room.  They were already moving, running like they could make their way downstairs and escape out the front doors.



I drew my knife, stepping into their path.



``Weaver?''



My bugs flowed past them.  I could see, hear, smell, taste.



The swarm went on the attack.  People in the crowd screamed and ran.



Of the three I'd targeted in their midst, I saw one open his mouth wide.  Four small trilobite parasites crawled out, dropping to the ground.



His nostril bulged, and one crawled from his nasal cavity.    One crawled from each of his ears.



His pants bulged, a great deal in the back, then a little in front.  They fell out of the bottom of his pant legs.



The others were producing some now too.



Crucible caught the first in his forcefield.  He paused a second, then turned it on full burn.  The forcefield dissipated, and man, parasites and a circular section of floor were scorched black.



The other two were still fighting off the bugs when Crucible burned them as well.



Silence reigned.  The crowd, I think, was a little too horrified to cheer for us.



``First kill?'' Imp asked, quiet.



``Yeah''



``How the fuck did you get to be a hero with a power like that?''



``Kept it a secret from you guys, kept it a secret from the public.  You can do a lot with a solid forcefield bubble.''



Grue and Clockblocker joined me as we approached the coffin.



It opened easily, and we stepped back, as Crucible surrounded it in a bubble.



\emph{Jack}?



He lay inside, opened his eyes, and frowned.



``This didn't go according to plan,'' he said.



I could see the forcefield start to change hues, ready to bake before Jack could say anything devastating.



``Stop,'' I said.



``But the idea was-''



``Just stop.  It's not him.  Doesn't fit.''



Jack only smiled.  ``That so?  \emph{Well}, it's the bug girl.  I can't even remember your name.''



I could see the tension in the other's bodies.



He stepped forward, staggered a little, then poked at the forcefield bubble with his knife.



``Shall we put an end to all of this?  You got me.  Victory is yours.  Murder me, and they all go off leash.''



``It's not Jack,'' I repeated myself.  ``It's Nyx's power.''



Jack's expression became a frown.  Then he dissipated.



It was only a teenager, trapped inside.  He was in the middle of asking a question.  ``-you let me out?''



``Holy fuck.  I almost burned him,'' Crucible said.



The boy pounded one hand on the forcefield.  ``Please!''



``I'll let him out,'' Crucible said.



I hesitated, holding up a hand.



No.  Not enough grounding to say for sure.  I let my hand drop.



``Weaver?''



I was about to give the go-ahead, but Tattletale's voice came over the comm.  ``\emph{That's Nyx you're looking at.  Her range is too short, she'd have to be in the building, and she's too distinctive looking to pass in a crowd.}''



I stared at the teenage boy.  I'd almost said he could leave.



``Last chance, Nyx,'' I told the `boy'.  ``Last words?  Share a juicy tidbit?''



The `boy' faded away.  \emph{An illusion in an illusion}.  It was only a woman with pale red skin, overlarge black eyes and vents along her hairline, the back of her neck and down the backs of her arms.  A fog seeped out from the holes.  A small Cauldron emblem was tattooed on her face like a beauty mark.



``No way I can convince you to let me go?''



``You could,'' I said.



``Hey,'' Grue said.  ``She's too dangerous.''



``For good enough information?  I'm willing to risk it.''



``I agree,'' Clockblocker said.



``Good information?''



``Tell us where Jack is,'' I told her.



She smiled.  ``And I get to go free?''



``My word as a hero,'' Clockblocker answered her.



``He's on his way to visit Nilbog.''



``\emph{It's true},'' Tattletale said.



``Now let me go,'' Nyx said.  She rolled her shoulders, ``Take me into custody, if you have to.  All I want is to live.''



``No,'' Grue said.  ``We can't let her go.''



``No,'' Clockblocker agreed.  ``Crucible?''



Nyx snarled, and the fog blasted out of the vents along her body, forming into a shape.



She didn't get any further before the orb flared.  Her scream was high, loud, and exceedingly brief.



``Nilbog,'' I said.





