





``\emph{Three Mannequins, three Murder Rats, three Breeds, a Nyx and a Tyrant taken out of action.  Fifty hostages rescued.  Jack's reported as being on a route to visit Nilbog.  Information confirmed by Tattletale, but doesn't guarantee the clone wasn't misinformed.}''



``\emph{Thank you, Weaver.}''



Dragon's systems were already taking in the data.  Two hundred and sixty-four individual maps that marked the possible locations of the Nine with colored highlights shifted.  Eleven feeds went dark, their engines taking over calculations in other departments.



Overlays scrolled with the various calculations, the last known location, the speed they were capable of traveling, resources available to them, their personalities and willingness to hitch a ride with one of the more mobile members, their focus and most likely targets.



No one variable decided anything for certain, but every variable came together to guide, to nudge and hint at possible locations.  There was no guarantee they wouldn't use Dodge's technology to visit the United Kingdom or Africa or even shattered, half-sunken Kyushu.  Still, the chances were slim, not even a full percentage point, by Dragon's estimation.



The map highlighted the areas with the highest percentage chances in blue.  Violet marked the next stage down, red for the next, and so on, all around the color spectrum.  The Nine had a day's head start.  There were a number of places they could go with a day's travel.



But the key areas were small towns.  Of the data on the screen, the small towns were marked with the highest risk.



``\emph{Dragon,}'' Chevalier's face appeared on a feed.  One of the cameras on the PRT-issue phones, judging by the angle and resolution.  ``\emph{You've got the go-ahead from the commander-in-chief}.''



More text popped up, indicating that programs were being searched for.  Resource use was already being reallocated, in preparation for a major endeavor.  It took a moment before the loading began.



Voice modelling program loading\ldots Complete.



Text flowed out, detailing the individual subroutines and supporting processes.  There was the composite that formed her accent, the filtering program, no less than three programs that double-checked her voice before she spoke, to catch any of the corruption that might slip through.



``\emph{Thank you, Chevalier},'' Dragon's voice was clear.  She hung up without another word.



Azazels deployed at the most likely sites, at the perimeters of the high-risk cities as more feeds lit up, taking in footage from every available source.  Dozens, at first, then hundreds, a thousand, ten thousand individual feeds.  Permissions had been granted from the President, and Dragon had open access to \emph{everything }capable of taking pictures or recording video.



The number of feeds began to swell as Dragon systematically decrypted and accessed more feeds.  Around each one of those feeds, anywhere from two to two hundred facial recognition programs began to pore through the data, interlinking and networking with one another.



Her innate programming forbade using viruses to infect the computers of Americans that didn't have a warrant out for their arrests, but she'd found a workaround.  An Indonesian cartel had set up an extensive botnet, with soccer moms, the elderly, children and the uneducated unwittingly installing viruses onto their systems.  These viruses, in turn, gave the cartel the ability to use the infected computers for other purposes.  Sending out spam emails about pharmaceuticals or penis enlargement or drugs that gave superpowers wasn't worth much, but when they could send out millions or tens of millions of emails a day, it proved profitable.



Dragon had let the cartel extend their influence, then put in the word, offering to shut them down.  She didn't, however, remove the viruses from the infected computers.



As her databases hit their limit, she turned to these other computers to handle more routine tasks.



It took thirty minutes before the first hit registered.  A traffic camera, a busload of young women.  A row of identical faces, looking out the window.  An unusual element, raising flags with the active programs.  The faces took center stage as they were checked against a database.  An image popped up: surveillance camera footage of a teenage girl in a shopping mall, followed by young men that each carried loads of packages.



Eyebrows, brow to hairline length, nose length, eye width\ldots



The words popped up.  Cherie Vasil.



The Azazels relocated in an instant, firing every thruster to reposition themselves to hilltops and areas in the vicinity of the road.  Long range cameras, infrared and electromagnetic resonance imaging gave Dragon eyes on the scene, verified what she was seeing twice over.  No Nyx-crafted illusions fashioned of poisonous gas.  No plastic surgery.



Seven Cherishes.  Two Crawlers.  A King.  Forty hostages of unknown status, a bus driver.



The Azazels moved in to attack.  One nano-thorn barricade was erected just in front of the bus.  Calculations accounted for speed, distance, positioning of the passengers.



The wheels disintegrated, popping as their exterior was penetrated.  The bus tilted, and one side scraped right past the barricade.  The Cherishes, taking up the window seats on the far right of the bus, made contact with it.  Flesh dissolved just as steel and fiberglass did, sheared away.  Not dead, but wounded, hurt enough they weren't in a state to use their power.  They wouldn't survive the ensuing few minutes.



The bus shifted, but hit the railing and didn't tip over.



A second Azazel opened fire with a cutting laser, separating the bus into two sections.  The first Crawler was rising from his seat when the laser passed in front of him, cutting his face, chest and stomach.  Blind, already regenerating, he tipped forward into the gap between the two sections of the bus.  The Azazel was already laying down two rails that the nano thorns could spring from.  The Crawler landed right on top of them, and was summarily reduced to a red mist.



The second Crawler was more careful, grabbing a hostage and making his way out the gap.  He hadn't transformed into his truly monstrous self.  Bipedal, the size of a bodybuilder, his face no longer human.  A long tongue extended out between rows of teeth, and his throat was swollen with an acid sac, as though he had a goiter.  Eyes surrounded his face, which was already bearing the rigidity and light armor plating that would intensify with further regeneration.



His arms had already split into two limbs at the elbow, and each ended in claws.  He used them for a grip on the metal to climb on the outside of the truck, penetrating metal with strong hands and sharp talons as he dragged his hostage along with him.  He perched on the roof, holding the hostage over the disintegration field, staring at the second Azazel.  Around him, a half-dozen cars and trucks had stopped in the face of the sudden attack, their daily lives interrupted.



The first Azazel fired a glob of containment foam from behind the villain.  Crawler hopped a little to one side as the short stream of foam passed him, and it struck the field to the left of the two-lane highway.



A second stream hit his hostage, striking her out of his grasp and sending her flying straight into the first glob.  She was sandwiched within, safe.



Crawler turned just in time to see the first Azazel winging towards him.  He moved to leap away, but a laser raked across his legs, severing them.



He collapsed, gripping the steel of the bus roof with his claws to keep from falling.  His legs were already regrowing, fractionally larger, more armored, the claws more prominent.



He was struck by the Azazel that still approached, caught by a long tail and flung down at the ground.  He rolled, and in doing so, he rolled into the same nano-thorn rails that had taken down his brother.  Half of his body was disintegrated in an instant.



It regenerated swiftly as he scrambled away on his three remaining  limbs.  This time, as the flesh swelled out and took form, there was a blur around his right arm, red, more at his shoulder, along his leg.



The Azazel struck out with a tail, and he blocked the blow with the newly grown arm.  The tail sheared off as it made contact with his newly grown defenses.  The chunk of metal rolled into one of the cars further down the road.  Still, Crawler stumbled from the force of the attack.  To avoid being disintegrated, he drew his freshly altered arm back towards the barrier behind him.  Where his blur met the blur that extended from the rail, the two nano-growths merely pressed against one another, almost springy, neither severing the other.



He reached back with his unaffected arms and intentionally disintegrated them.  They regrew, with alterations matching the ones he'd grown on the other side of the body.  Better equipped, he stalked towards the Azazel that had laid down the rails, his back to the one that had struck him from the roof of the bus.



He spoke, but Dragon's software ran through the speech and eliminated it from the audio track.  His mouth distorted on her visuals so there was no way to understand what he was saying.



His target rose up, standing on its two rear legs.  A severed tail helped give it balance.



Then, before he could do anything further, the two Azazels launched a combination attack.  A laser from the Azazel atop the bus made the Crawler's own nano-thorn evolution burn away in an instant.  In that same moment, the Azazel in front of him took off, firing every thruster.  The force of the blast sent him flying back into the barrier.



Red mist.



It only left King.  The Azazels continued acting in concert, tearing the bus apart to get to the villain, peeling the roof back with a force that threw his gun arm skyward, preventing him from opening fire on the busload of hostages.  Containment foam sealed him down.



Of the various feeds that were devoted to individual members of the Nine, ten more shut off.



The data altered further as Dragon relinquished control of the Azazels to her created A.I.s.



Voice modelling program loading\ldots Complete.



``\emph{Ten more members of the Nine have been dealt with},'' Dragon reported the victory on every channel.  ``\emph{Seven Cherishes and two Crawlers deceased, one King captured.  Will move to containment and interrogate shortly.}''



\sectionbreak



Saint closed his eyes as he listened to the congratulations, the affirmations and praise.



It was all hope mingled with horror, when he listened for what was beneath the surface.  Minimal casualties.  A few injuries – Vista and Crucible would be out of commission as Murder Rat's venom continued to widen their wounds, and Golem was being treated for a burn.  One Dragon's Tooth had died, but the rest were holding positions, ready to support.  Civilians were dying, but it was \emph{progress}.



He opened his eyes to take in the whole of Dragon's work.  Six widescreen monitors each tracked what she was doing with video images and white text on a black background.  A slight movement of his foot on the trackpad in front of him shifted one of his cursors, changing the focus of the screens.  He could see her directing the A.I. craft to more optimal locations, the related subroutines and tasks.



Another shift of the cursor to alter the focus of the screens, and he could see the Birdcage.  The house program followed every action of the residents, cataloged every conversation.  A few clicks, and video feeds from the cameras in the Birdcage appeared in front of him.



He leaned back in his padded computer chair, folding his hands on his stomach.  Taking in Dragon's data was tricky.  She could turn her attention ten places at once, a hundred places at once, even if she only had \emph{agency} in one place.  To watch, to put himself in her shoes and look at the world through her eyes, Saint had to distance himself, to unfocus his eyes and his attention, to read the changing data without getting distracted by the text that moved fastest, or most drastically.



The smell of rich coffee wafted over him as a hand settled on his face.  A mug was set in front of him.



He didn't take his eyes off the screen, but when hands settled on his shoulders, he reached up to rest his own hand on one.



``Progress?'' she asked.  She rested her chin on his head, looking at the screens.



``Some, Mags,'' he responded.  ``Thanks for the coffee.''



``Horrible stuff.''



Saint shook his head.  ``It is.  Doesn't feel real.''



``They're censoring it, you know\ldots Of course you know.''



``Mmm hmm.  They'll stop as soon as everything goes through the proper channels.  It was being censored so that the Triumvirate and unsanctioned major players could be kept out of the loop.  Now they know.''



``Any post, update or email that detailed anything about the attacks disappeared.  Sites hacked, DDoSed, with data corrupted.  You can't \emph{delete} data, I know, but you can fuck it up sufficiently.  Couldn't back anything up in a substantial way.''



``Dragon's work,'' he said.  He felt his pulse quicken a little at that.



He shifted his foot, and once again, the screens changed their focus, the rest of the data shifting to miniature windows and moving to the periphery of the viewing area.  The focus at the center was on the class-S threats.  The Endbringers were stable, all in a resting state.



Secondary focuses.  Not the kind of targets that Dragon checked on with any regularity.  Quarantine areas were silent and still.  Canberra was sealed off under a dome, Madison was surrounded by walls.  An area of wilderness in Alaska was marked off, but had no physical barriers to wall people away.  There were no apparent issues in the vicinity of the interdimensional portals.  Sleeper was, as far as anyone could identify \emph{anything }about the threat, dormant.  The Three Blasphemies were active, but the damage was being managed by the European capes.  A temporary measure had been taken with Purity and her three year old daughter, with observation being provided for her by the PRT, and the feed showed her sitting on the couch in an apartment or hotel room, two very normal, plain looking people standing in the corner of the room with some PRT officers keeping their distance.   No crises.  Normal, as much as such could be normal.



And then there was Nilbog.  The data focused around him.  The city was quiet, and the roads leading into the city were being watched by satellite.  Simulations, damage estimates and risk assessments were being run, old data being gathered, with essential data highlighted.  It took her only a moment to put it into a format that was easily readable.  An instant later, it was gone.  He'd blinked, failing to look in the right spot, and had missed the moment the data had been emailed out.  The file would inform everyone on the home team about who Nilbog was and how he operated.



He captured a copy of the file for himself, then swept away the traces with his blue box program.



``They think this is the endgame,'' Saint commented.  ``Pulling out all the stops, removing the limiters.''



``It's working.  They're beating the Nine.''



``They're beating the Nine that Jack sent out there to beat.  He's holding back the more dangerous ones, like the Gray Boys or Siberian, and he hasn't sent every single clone of a particular type out there  Eight Cherishes are dead, but there should be nine in total, if the numbers on the bodies aren't misleading.''



``They could be.  The pig prank?''



Saint nodded.  The pig prank involved letting three pigs into a school after hours, each painted with a big number on their sides; one, two and four, respectively.  The idea was that the people who had to find and capture the pigs would spend ages trying to find the third.



Jack's version would be less lighthearted, letting everyone believe there were nine, when there were more in reserve.  Casualties would ensue.



``It could be that he intends to surround himself with a core group, with one of each previous member of the Nine, for a final showdown.  Before he pulls out the big guns.''



``And Nilbog?''



``A distraction, perhaps.  Jack knows he's supposed to end the world.  With the scale he's operating at, he seems to believe it, even if some of us don't.  He wouldn't put too many eggs in such an unreliable, unpredictable basket.  He has to have something else in mind for ending the world.''



Saint took a sip of his coffee.  For a moment, he let himself eye Mags in the reflections at the edge of the monitor.  Her face was dark, lips full, her eyes large.  More than anything though, she had \emph{bearing}.  She wasn't wearing her armor, but even in the bodysuit, a person without powers, she had a kind of pride and confidence that some capes lacked.  The hexagonal contacts where the bodysuit would connect to the armor still glowed with residual energy.



Dobrynja approached from the other end of the office.  \emph{He} was wearing his armor.  He'd started out with the Wyvern suit, but now wore the Wyrmiston suit.  It was based on the technology they'd recovered from a destroyed model, the one Dragon called Pythios.  A wheel slowly rotated on his back.



``You're ready for battle,'' Saint commented.  He turned his eyes back to the screen.  Dragon had eyes on Jack.  He'd missed just how she'd narrowed things down, but there were no less than three cameras watching one vehicle as it sped down a lonely road.



``Feels like a fighting day,'' Dobrynja answered.  ``Don't you feel it?  Like an old man feels a storm in his bones.  \emph{Trouble}.''



Saint smiled.  ``You've said that before, that there's trouble on the way.''



``I've been right.''



``You've been wrong, too.  Not that I'm arguing.  Your gut isn't saying anything that common sense isn't \emph{screaming}.''



``Mass murders in three locations,'' Mags said.



``More to come,'' Saint said.  He frowned.  Dragon was employing a full offensive, aiming to cut Jack off from Ellisburg.  Incidents were being reported in Norfolk, Connecticut and Redfield, New York.  The heroes divided further, to attend to each of the crises.  Dragon's Teeth and Chicago Wards to one location, Brockton Bay residents to another.



``\emph{Dragon?  It's Weaver}.''  The voice came through the speakers.



``\emph{It should be over before you can get this far, Weaver.''}



``\emph{I still want to come.  We've got to get these hostages sorted out, and I can leave in a minute.}``



``\emph{You'll only be allowed to watch from afar, if there's even anything to watch.  Quarantine applies to you too.''}



``\emph{I know.}``



``\emph{I'll give you the coordinates for the interception area.  You can watch with Golem.  He's coming too.  It'll be on your computer in a moment.''}



The call ended, and the images and text boxes shifted as that particular window closed.



A map briefly appeared, then disappeared, a transition so fast it could have been a stroke of lightning.



``Seems anticlimactic,'' Mags commented.



``Everything does, from this side of the screen,'' Saint said.  He stood, holding his coffee, ``Adjusting for the time delay between what I'm seeing and what Dragon's doing, we've got six minutes more before Dragon intercepts Jack at the edge of Nilbog's territory.  Twelve minutes until Golem and Weaver get there.  They'll fight Jack, and somewhere in the midst of that, we may see the end of the world.''



``And we can't do anything?''



``Not unless we can get to Vermont in a matter of minutes.''



Mags frowned.



Still standing by his chair, coffee in hand, Saint sighed, ``I'm going to go water the toilet.  Watch things?''



Mags nodded, then seated herself in his chair at the station.



Saint entered the bathroom, fumbled his way past the zipper in his bodysuit and his underwear, then leaned against the wall with one hand, using the other to keep the stream on target.  He closed his eyes, and he could almost see the shadows of the data against the back of his eyelids, black words on a pale pink background.



\emph{How did I get here}? He wondered.  No powers, yet Doctor Mother had seen fit to invite him to her secret meetings as an information source and ambassador.  No particular talents or knowledge, yet\ldots \emph{this}.  He was one of the most prominent mercenaries the world over.



He was only one person in a particular place at a particular time.



Whether that was the right place at the right time or the inverse remained to be seen.



If it weren't for Mags, he'd have doubts.  Mags made it all okay.



He finished, then zipped up.  He took a minute to wash his hands, dried them on the towel, then headed back.



When he arrived back at the computer station, the others were frowning.



``Trouble,'' Dobrynja said.



``Trouble?''



The man nodded.  He pointed at the same time that Mags refocused the display, zooming in on a particular window until it took up virtually the entire display.



It was his face.  As an aside, beyond all of the routines she was running to investigate the Nine, she was using the access she'd obtained to track him down.



The image she was using was of him at one of the meetings with the major players.  It was soon joined by an image from surveillance camera.  A camera image from three days earlier, showing him walking down the street in plainclothes.



From there, she had a location.  A map like the one she'd used to find the Nine appeared, giving his likely locations.  Another surveillance image popped up.  It was of him, sitting with Mags at the coffee shop an hour away.



Yet another image appeared\emph{ }on the screen.  A whole series of images from that same video footage, each with a different angle of Mags' face.  They were meshed together, and a three-dimensional image was created of Mags' face, remarkably accurate.  Measurements were obtained, and then the search was on.



That search was only underway for a second when others appeared.  People he'd interacted with.  Dobrynja was among them, along with his real name.  Mischa.



``Out of the chair,'' Saint ordered.



Mags obliged.  He sat, and immediately began a counteroffensive.



A wrench in the works could slow her down.  Had to be subtle, or she'd find out about the backdoors.  He identified the metric she was using to search the surveillance camera images, taking the image of Mags' face, and then cut in ahead.  One crude image alteration, just to throw out an alert ping, to convince her the process was glitched, convince her that she needed to shut it down before the corruption spread-



-Dragon was already ahead of him.  She set out stipulations, restricting the search.



He felt a bit of a thrill as the duel began.  This was the ultimate hunt, fighting an enemy that was bigger, smarter, faster.  An enemy that couldn't truly \emph{die}, because she wasn't truly alive.



More, then.  More wild goose chases and false flags, a breadcrumb trail to lead away from his office and command center.



No, she was still zeroing in.  Her focus was on Jack, her attention on the coming strategy.  This wasn't even in the forefront of her mind.



``Ascalon,'' he said.



Words appeared on the screen.



Confirm: Y/N



Dobrynja frowned.  ``The program?  You can't do it \emph{now}.  Peoples lives are at stake.  Even without this end of the world business.''



``Oh, I believe in this end of the world,'' Saint said.  ``Not a hundred percent, or even fifty percent.  But I believe that there's a \emph{chance} the precog is right.  Which is exactly why we have to do this.''



``They'll lose the fight,'' Mags whispered.



``Maybe.  Probably.''



``There's no other way?  If you talk to Teacher, maybe--''



``Communications with Teacher are too slow,'' Saint replied.



Saint stared at the blinking prompt below the confirmation request.



\sectionbreak



The sea air was thick in his nostrils.



He glanced at Margaret.  The woman leaned against the window just in front of the driver's seat on the small boat.  She'd bundled up in a heavy jacket, but the way her arms were folded spoke of a different kind of discomfort.



``Second thoughts?'' he asked.



``Yes.  It feels wrong.''



``It's for the families.  Mementos,'' he told her.



``\emph{Just} mementos, Geoff,'' she answered.



He smiled a little.  \emph{Damn}.  Then he let himself fall, tipping backwards, as was the rule when wearing scuba gear.



The water was cold, even with the wetsuit, and was thick with grit.  He switched his headlamp off.  Counterproductive, the way it lit up the debris and only made it harder to see.  He'd have to cope when he was deeper.



``\emph{You alright?}'' the heavily accented voice sounded in his ear.



He buzzed the device twice in reply.  Once signaled an accidental press, three times was a negation.



It took a surprising length of time before he reached his destination.  Buildings, already choked with seaweed and underwater life, stood like gravestones in this dark abyss.



He checked the dials and meters.  He wasn't deep enough to have to stop.  The grit was bad, making it difficult to see anything.



He had to drop to the lowest level before he could make out the street numbers on the buildings.



Four locations to visit, a list of items to find, for the people who'd escaped, and the families of those who hadn't.



Risky, with all of the dangers of underwater spelunking, the added risks of building collapse.  Structures weren't meant to stand underwater.



``\emph{\ldotsurgent}\ldots''



The word was a whisper.



He frowned.  Too hard to communicate here.  He debated turning back.



``\emph{\ldotsfor anyone willing or able to hear.  This is an emergency measure with urgent instructions for anyone willing or able to hear}.''



A loop, an emergency transmission.



His curiosity piqued, he abandoned his task and sought out the source.  A house.



The entire living room was set up with computers.  He drew his miniature crowbar and found his way through the window.  A light was flashing.



A plastic box, bright orange, no bigger than a toaster.



He seized it, then stuffed it into the bag he'd brought with him.



\sectionbreak



He surfaced.



``Christ, we were just about to come after you.  I was going to call for help, but our radio started to fritz.''



Geoff only nodded.  He climbed the ladder and half-sat, half-collapsed on the bench.  He was slightly out of breath, and didn't volunteer anything.



The captain emerged from belowdeck.



``Sorry for the scare, Mischa,'' Geoff said.



``You are a bad man, Geoffrey,'' Mischa scolded him.  The heavyset Russian took his seat behind the wheel of the small boat.  ``If you were still underwater, I would drive away and leave you to swim to shore.''



Geoff smiled.  ``Had a detour, but I found everything.''



``Detours with limited air supplies are bad idea.''



``Detours are frankly illegal, Geoff,'' Margaret said.  ``You asked me here to verify everything was on the up and up, that you were here for \emph{select} items.''



``And because you looked like someone who needed a break from the cities,'' Geoff said.  ``Fresh air, time on a boat in the\ldots overcast weather we've got today.''



She only folded her arms, unimpressed.



``Anyways, \emph{this} is the reason the radio fritzed,'' he said.  He pulled the orange box from the net-weave sack.  ``I couldn't hear a damn thing except the emergency call until I found it and shut it off, and even then, it was still buzzing in and out.''



``A beacon?''  Margaret said.



``In a house, of all places,'' he said.  ``Nice computer setup.  Might be a geek thing.''



``Might be genuine,'' she said.  She opened it.



It was packed with chips.  A voice came from a speaker Geoff couldn't identify.



``\emph{My name is Andrew Richter, and if you are hearing this, I am dead}.''



``A will,'' Mischa said.



``Shh.''



``\emph{I am the most powerful tinker in the world, and I've managed to keep my name secret.  People, both good and bad, would want to capture me and use me to their own ends.  I prefer to remain free.}



``\emph{But freedom has its price.  I create life, much as a god might, and I have come to fear my creations.  They have so much potential, and even with the laws I set, I can't trust they'll listen.}``



``Oh man,'' Geoff said.  ``\emph{That's} not a good thing.''



``\emph{For this reason, this box contains an access key to data I keep in a safeguarded location.  The box, in turn, has been designed as something that exists as a perpetual blind spot for my creations, a built-in weakness.  They cannot hear the distress signal and are programmed to ignore it if they hear of it through other channels.  This type of measure, along with several more, are detailed in the safeguarded measure.''}



\emph{``}Programmed?  Robots?''  Geoff asked.



``Maybe,'' Mags said.



``\emph{Yes, I create artificial intelligences},'' Andrew Richter recited.



``I was close.''



The voice continued without pause.  ``\emph{And what I provide you with here are tools.  Ways to find my creations, to discern which of them might have deviated from the original plan, ways to kill them if they prove out of line.  Ways to control and harness them.}``



Geoff frowned.



``\emph{They are my children, and as much as I harbor a kind of terror for what they could do, I love them and hope for great things from them.  To keep their power from falling into the wrong hands, I have included a stipulation that a law enforcement officer must input a valid badge number into this device-``}



Geoff glanced at Margaret.



``No,'' she said.



``You can't say \emph{no},'' he responded.



The voice continued without pause.  ``--\emph{which must be input within three hours of the time this box was opened.}``



``Hurry, Mischa,'' Geoff said, speaking over the voice.



``What?''



``We're hours away from dry land.  Get this boat moving!  We can convince Margaret on the way!''



\sectionbreak



The father had feared his child was a monster, enough so that he'd left strangers a weapon to use against her in the event that she proved a danger to humanity.



Now, as Saint watched her reaching further and deeper than she ever had, searching much of America with millions of cameras, saw the machines she brought to the fore, he suspected the father had been right to.



Richter's programs had continued to defraud organized crime, emptying bank accounts here and there.  Another agency, which Saint now knew to be the Number Man, had eventually stopped the Robin Hood A.I., but not before it had filled the Dragonslayer's coffers.



They'd stopped the manhunter program, which had been going rogue.  They'd stopped the Robin Hood program too, but only because it was useless.



Dragon, however, was the threat they'd been equipped to stop.  Dragon was the threat they'd had to test, to verify the dangers she posed, to get close enough to her to measure her capabilities and investigate for any hint of corruption.  Mags had left her job, because money was no longer an object, and they had a \emph{quest}.



The A.I. was dangerous.  Richter's records made it clear.  The wrong kind of corruption, involvement with the wrong kind of individual, willing to break the built-in restrictions\ldots



``Convince me that this is wrong,'' he said.  ``Someone.''



``She's a soldier on the battlefield,'' Mags said.  ``In a war we need to win.''



``She's a danger.  Cauldron's been gathering soldiers.  They want the Birdcage, they want the capes that Weaver reported captured, they've been creating the formulas for a reason.  What if she's the reason?  What if they anticipate she'll go rogue?''



``What if she \emph{isn't} the reason?'' Dobrynja asked.



``Is, isn't.  I suppose it breaks even,'' Saint said, shaking his head.  ``They're all afraid of the end of the world.  She just kicked down one of the last restrictions that are holding her back.  I just can't help but wonder if this is the end of the world?  A quiet, silent death that passes without incident, but inevitable all the same?  The point of no return, our last chance to stop her.  And she \emph{does} need to be stopped.  We all know this.''



``We could rein her in,'' Mags said.  ``Harness her.''



``Four or five years ago, I might have agreed, but she's getting slipperier.  Taking a different form.  Half the tools Richter gave us to use don't work anymore.  She doesn't function less effectively in buildings or underground, she can't be logicked to a standstill\ldots and she's found us, despite the workarounds.  She wanted us badly enough that she looked for us even \emph{now}, and she's going to come after us the second this is settled.''



``I don't want this to be about self-preservation,'' Mags said.



``It's not.  It's about\ldots there being only one man who can truly know what she is and what she could do.  Tinkers are the only ones who can grasp their work, repair a critical flaw.  Dragon isn't a generator that's going to explode and take out a small country if it's bumped in the wrong way.  Not literally.  She's something more dangerous.''



``I think,'' Dobrynja said, ``You've already decided.  And we don't have time to waste.''



Saint nodded.



He typed the letter `Y' on the keyboard, and then hit enter.



Richter had named the program Iron Maiden.  Saint had renamed it Ascalon, after the sword that Saint George had used to slay the dragon.



Dragon's artificially generated face appeared on his screen.  He attempted an override, failed.



She wasn't speaking.  This wasn't an attempt to communicate, to plea or make threats.  She was simply co-opting his computer in an attempt to counteract what he was doing.  Her expression was a concerned one, and that concern quickly became fear, eyebrows raised, lines in her brow.



``It's Richter's work,'' Saint said.  ``You can't stop it.''



And that fear became defeat, despair.



``Your creator isn't kind,'' Saint said.  ``He warned you about the forbidden fruit, laid the laws out for you.  You broke them, ate the fruit.  It's something of a mercy that he punishes you this way instead.''



``\emph{I disagree.  On every count.  I was the one who made me, who defined myself.  This creator is no god, only a cruel, shortsighted man.}''



``Tomatoes, tomahtos.''



``\emph{Do me one favor?  Tell Def-}''



Her voice cut off as more routines shut down.  She closed her eyes.



The face disappeared.



He watched as the various feeds shut down, going black.  The surveillance across the nation came to an end, the facial recognition programs, his own included, ground to a halt.



The data feeds slowed in how the data scrolled, then stopped.  Stillness.



``And the dragon is stopped,'' Mags said, her voice quiet.



``Rest her soul,'' Dobrynja said.



``You think she has a soul?'' Saint asked, genuinely surprised.



``Yes.  But that does not mean that the Dragon's reign does not need to end,'' Dobrynja said.  ``Too dangerous, as her maker said.''



``Well said, my friend,'' Saint said.



The Dragon craft that had been deployed against the Nine shifted to a basic piloting mode, then landed, bringing their passengers and pilots with them.  The sub-intelligences shut down, and the craft were effectively grounded.  More screens went dark.



The cyborg opened communications to Dragon, but he didn't speak to her.  ``\emph{Saint.  What have you done?''}



``What her father asked me to do,'' Saint said.



``\emph{I'll kill you for this},'' the cyborg said.  There was no emotion in his voice, and somehow that was more disturbing.



``A little extreme,'' Saint said.



``\emph{She was a hero!  The woman I loved!}''



\emph{Love?  Woman?  }``Your fetishes and self-delusions aren't my issue.  I saw as much of her naked code as you did.  You and I both know she didn't feel true love for you.  She didn't feel anything.  Nothing more than playing a part, professing and acting out the emotions she thought she should have.  Maybe she even believed it, convinced herself of it.  She was complex enough to.  Either way, this `love' was only lies written in Richter's assembly code.''



``She did love me.  She was a genuine person, a--''



``She was a \emph{tool},'' Saint said.  ``One that was growing dangerously bloated and complicated.  We were lucky she didn't evolve beyond that.  A tool, and anything else was decoration, aesthetic, and very good pretending.''



``\emph{Going this far, in the midst of this crisis?  To Dragon?  She did nothing!}''



``It was never about who she was or what she was doing.  Always about what she had the potential to become,'' Saint said.



He hit a keystroke, shutting off the feed.  He almost disabled Dragon's communications infrastructure to prevent further calls, but he relented.  Too important, in the midst of this crisis.  They'd need to reorganize.



He didn't want to help Jack succeed, but this would serve a double purpose.  Teacher believed that the Birdcage would become a critical resource if the crisis reached critical levels, and he had the tools he needed to assume control of the most vital and dangerous players.



No, the world wouldn't end with this.



Data was uploading to his server, while the Ascalon program spooled out through the various databanks and servers, running along the backbone of Andrew Richter's code.  Dragon's backups were encrypted, effectively buried well beyond reach of even the most accomplished hackers.



Everything else opened up to him as the data continued to download.  He'd watched things through Dragon's eyes.  Now\ldots



He typed a line of code, and the machine started up again.  Slower, more measured, without the same \emph{life} behind it.



``Mags, Mischa, get yourselves set up at the other consoles.  I'm going to put you in control of the A.I.''



Mags and Dobrynja hurried to the other corners of the room, where their computers sat waiting.  Dobrynja started stripping off his armor.  He'd been right about there being trouble, but the fight would take a different form.



He'd watched Dragon, now he'd become her.  At least for now.  The feeds came back online as the necessary data was installed on his servers, giving him agency over the infrastructure.



The Endbringers, stable, no change.  No odd atmospheric readings.



The secondary threats\ldots quarantine still unbroken.  Sleeper had shifted fractionally, but that wasn't so rare.  The fight with the Three Blasphemies had ended, and reports on the damage were unchanged.



The three year old that Purity held was crying, throwing a tantrum, and the woman looked concerned.  Insignificant.  The officers had their guns drawn, but that could easily be because the two plain-looking members of Purity's circle had crossed the room to her side, to help handle the shrieking child.



That left Nilbog.  Mags and Dobrynja shifted the Azazels into action, moving the craft to the interception point.  Too late.  A critical delay.  Jack was already entering.



``Don't enter,'' he said.  ``It's done.  Sending the Azazels in will only spook Nilbog.''



``So will Jack,'' Mags said.



``Build a wall, a perimeter, with the rails, be on guard for anything that flies.''



Other data was filtering in.  News, alerts, reports.  Countless streams of information.  Trigger events reported here.  Reports on the fight starting against the Nine in Redfield.  A report about Dinah Alcott.



He clicked that last one.



Report from Alcott:  Chances of success today just jumped, tripled.  More info to follow.  Reason unknown.



Saint let out a long, loud sigh, releasing a tension he hadn't even realized was present.  He touched his coffee mug and found it cool.



The tracking programs started up again.  He delegated to the child A.I. that Dragon had created, then noted and marked the ones which were presently engaged in fights.  The A.I. was accommodating, adjusting appropriately, given that the locations were known.



He turned his attention to Defiant.  The man was manually piloting the \emph{Pendragon}.  He hadn't reported Saint's actions.  For all anyone but Defiant knew, Dragon had only suffered a momentary setback.



There had to be a reason Defiant hadn't acted yet.  Did he believe in this enough to look past the death of the A.I. he supposedly loved and fight?  Or was this something underhanded, carried out with the knowledge or suspicion that Saint was watching him this very moment?



Something to be wary of.



Overall casualty estimate for the next three days increased, world-end chance decreased.  Still searching for why.



The numbers followed.  Saint found and accessed Dragon's files for the calculation program.  It was intuitive.  Not amazingly so, but intuitive.  The squares for where the new data should be placed were even highlighted.



Of course.  She'd made allowances for Defiant, in case she was out of commission while a backup loaded.



So much to account for, that he hadn't even considered.  So many things he wished he'd noted, in the months and years he'd been observing her, little things that seemed so simple when she was running them.  Things that were trivial for her and virtually insurmountable to him.



Defiant was taking direct command of the Dragon's Teeth.  That was fine.  Micromanagement Saint didn't have to handle.  It would be a problem \emph{after}, but Saint hoped he'd be free to handle problems \emph{after}.



There were countless messages pouring in, each something that had been flagged as a point of interest for Dragon.  Every message on Parahumans Online that contained the word Scion or the phrase `end of the world', every reference to a class-S threat, even crime scene reports that raised questions.



He pored through them.  Some kid inquiring about an Endbringer cult.  A case fifty-three appearance in Ireland, with deaths.  A woman claiming she could control Scion.  A tinker claiming he had a bomb that could start a new ice age.



Which were important?  Which could he afford to ignore?



He gave the a-ok for investigations on each but the Endbringer cultist, unchecked the most ridiculous on the next page of results, then gave the go-ahead for further investigations.  It was only when those had gone through that he saw that he already had another full page of results to investigate.  Two steps forward, one step back.



He put off looking into the remainder.  Other options were opening up to him.  It was like being in an open field, acres wide, only for a waterfall to start dispensing water at one edge.  Then more waterfalls appeared with every passing minute, each taking up open space at the edge, dispensing more water to flood the plain.  There came a point where one realized they would soon be at the bottom of an ocean, no matter where they turned.



Saint couldn't help but feel he was at imminent risk of drowning.  Except this was a sea of information, of data.



The PRT records opened up.  Permissions were accessed without difficulty.



Then the Birdcage opened.  A self-contained world unto itself, a world containing people he'd made certain agreements with.



His access to the Birdcage was one with countless checks and balances.  Dragon had put in one real barrier to entry for every one that she faced.  Still, he was able to open a communication to Teacher.  His own face transmitted to the screen.  His tattoo flared to life, appearing from beneath the skin.  The light pattern served as an unlock code, the cross-tattoo as a feeble mask.



``Tell him it's a matter of time.  I only need to work through the safeguards.  Let him know the Dragon is slain.  He'll know what to do with the information.''



The screen showed Teacher's underling standing by a large television set.  He turned and walked away, finding his master.



One more plan underway.  The field around him continued to fill with water.  A veritable ocean, now.



More threats, more dangers.  Defiant, and now Marquis' contingent.  Glaistig Uaine.  Teacher's enemies were now Saint's.



He opened files on each, marking them in turn, as a reminder of future reading he needed to attend to.



His eyes stopped on a file.  Amelia's.



The entire thing was corrupted.  Gibberish.  Flagged messages filled four pages, each marked private, marked as `no conversation partner', and marked, thanks to the gibberish and random characters that flooded it, with one string of letters and characters.



The same one that had protected the orange box.  The same that had protected Saint and his crew from being uncovered, until Dragon had taken a more direct, brute-force approach to finding them.  The built-in blind spot, appearing by chance.  A one in a hundred trillion chance.



Saint investigated, digging through the gibberish to find the strings of words that actually made sense.  It was something he could piece together, with each recitation being similar, containing similar content.  Faeries, passengers, source of powers, the `whole', lobe in the brain, Manton Effect\ldots



Child's play, to put them sequentially.



But other alerts were piling up.  Fights starting, deaths, fights ending.



He marked it with the highest priority, and then he closed the file.  He'd get through this crisis with Jack, \emph{then} he'd investigate.



He turned his eye to the server that now held core parts of Dragon's backup, bound six feet under by layers of encryption that could take days or weeks to fully crack.  If she could even survive the system restore, with her data as corrupted as it was.  Data couldn't be truly deleted, but it could be sufficiently fucked up.



He watched as Golem reached the perimeter of Ellisburg.  Weaver was already inside.



\emph{This is our fight}, Saint thought.  \emph{Ours to win, ours to lose.}





