





Ellisburg loomed before me.  A small town, surrounded by a massive wall.  Ellisburg had been situated by a river, and the wall included a section of the waterway.  The building that managed the flow of water was bigger than any structure within the walls, a filtration and guard system that ensured that nothing was making its way up or downstream from the small town.



It was a risk to even have the measure, no doubt, and it would cost money to operate and maintain.  There had to be a reason they had included the river rather than section the river off altogether.  A compromise?  Something to keep the goblin king happy?



I'd only been a toddler when the walls had first gone up.  Outside of that bit of news, the Ellisburg situation wasn't one that came up a lot, yet it had somehow found traction in the public consciousness.  It was something we all thought about from time to time, something that loomed as a possibility in everyone's mind.



Would today be the day the wrong person got too much power?



Would today be the day our hometown was effectively removed from the map, surrounded by sixty-foot concrete walls?



The dashboard indicated the Dragonfly was now approaching the designated landing point.  The A.I. had suddenly decided to ground itself, landing in a nearby field, costing me precious minutes, while Dragon had been silent on the comms.  I'd left a message, trusting her A.I. to pass it on, and hadn't received a response yet.



My attempts to patch into the feeds and get a view on what was going on with Jack hit a brick wall.  The corner of the monitor still showed the cube folding through itself in the corner, Dragon's loading message, as if the process had hung.



I'd manually piloted the craft back out of the field, and the A.I. had kicked in to handle the flight codes and necessary messages to air traffic control and nearby aircraft.  When I'd input my destination for the \emph{second} time, the craft mobilized.



But the silence, the strange blip in the A.I.'s direction, it left me uneasy.



Now, as we took a circuitous route around Ellisburg, to a field beside the large filtration and security building, I could see the Azazels, parked at the edges of the same location.



That was the point I felt \emph{alarmed}.



I hit the button on the console/dashboard. ``Dragon?  Requesting confirmation on the situation.  You intended to intercept Jack before I got here, but the Azazels are dormant.''



No response.



``Dragonfly,'' I said.  ``Display non-system processes and tasks last carried out.''



It displayed a list.  In a matter of seconds, the scroll bar was barely a \emph{line}, with thousands of individual instructions noted in collapsed menus.  A prompt reminded me I could load more with a request.



``In the last minute.''



The list wasn't much shorter.



``Communications-related.''



There.  Besides the orders I'd just given, I could see the message I'd sent to Dragon.



``Status of message?  Has she heard or read it?''



The loading symbol appeared in the corner.  It should have been nigh-instantaneous.



``Cancel that.  Give me manual access.''



A keyboard appeared on the dashboard.  I couldn't use it right away, though.  I was forced to pay attention as the Dragonfly reached the field and hovered.  I lowered the ship down.  The small craft shuddered as it touched ground.



Using the keyboard and the manual access, I began digging through the data.  I navigated the menu the A.I. had provided, then opened the submenu to view the details on the message I'd left Dragon.



My message was in the priority queue, but it sat at the 89th position on the list of messages Dragon would be getting to.



I dug a little, and found the list was growing.  Ninety-four, ninety-five\ldots



Where the hell was Jack?  I contacted Defiant.



``\emph{Defiant here}.''



``Weaver.  What happened?  Is the Slaughterhouse Nine situation resolved?''



``No.  He entered Ellisburg.''



I closed my eyes for a second.  It took a moment to compose myself and get my thoughts and priorities in order.  ``And the suits?''



``\emph{Ignore the Azazels.}\emph{Listen.  I've got a lot to handle and coordinate right now},'' Defiant said.  Was there a tremor of emotion in his voice there?  ``\emph{Golem's on his way.  Wait for backup.  I'm sending Dragon's Teeth your way.  Teams from across America are joining the fight now that the full situation is leaking. I'm putting some on containment and quarantine detail, make sure the Slaughterhouse Nine situation doesn't get beyond the areas the attacks are directed at.  I'm going to send a few your way.  Ten minutes.}''



``Jack's already in the city, and you want me to wait ten minutes?  That long, and Jack could get what he wants.  I've got the Azazels nearby if there's trouble-''



``\emph{The Azazels aren't\ldots reliable.  Consider them compromised, but a non-threat at the same time.  Listen, there are things I need to take-}''



``\emph{This} is the highest priority,'' I said.  ``Isn't it?  Jack?  The end of the world?''



A pause.  ``\emph{Yes.  Of course.  But I can't help you while I'm on the phone.}''



A note of deceit in that.  He was covering for something.



\emph{Something happened}.



I thought of what had happened at the school, the way Dragon had stopped abruptly.  I'd read the records, knew the gist of the story.  Dragon had been in Newfoundland when Leviathan sank it, had escaped, only to shut herself away from the world, never venturing outside the expansive building complex she'd had constructed in Vancouver.



She hadn't left Newfoundland unscathed, I was almost certain.  Brain problems, body problems\ldots I couldn't be sure.  Probably both.  She had no doubt integrated herself with technology to cope, enhance and expand her capabilities.



Except that her technology was failing.  The way she'd collapsed at the school, the speech problems she'd suffered, the slow recovery, now this\ldots  It was the only theory that made sense.



She'd pushed herself too far, something had gone wrong, and now Defiant faced losing the one person on this planet who could tolerate him for more than ten minutes at a time.  No small wonder he was out of sorts.



I considered how I'd feel if it was one of the Undersiders.



``Defiant,'' I said.  ``I'm going in alone.  Send Golem in after me if he wants to come, reinforcements can hang back or come with, depending on your judgement.  I'll handle things on this end.  You focus on what you need to.  Focus on Dragon, focus on damage control.''



A pause.  ``\emph{There's nothing I can do for Dragon right this moment.  The best I can do is maintain the momentum and keep things coordinated, and hope that Dragon's substitution can maintain the back-end}.''



I didn't respond to that.  I was already getting ready to go.



``\emph{Thank you, Weaver.}''



It was uncharacteristic of him to thank me.  A \emph{pleasantry}.  How upset \emph{was} he?



I couldn't spare another thought on the subject.  I was out of the Dragonfly at the first opportunity, making my way towards the quarantine control and filtration building.  It was squat, concrete, hardly pretty.  As I got closer, I could hear an alarm.



The front doors had been torn apart.  It might not have been so impressive, but these were the same vault doors we saw with the shelters that studded every likely target around the world.



The gouges were narrow, a finger's width, as though someone had dragged their hands through the steel like I could drag my fingers through half-melted butter.  \emph{Siberian}.



Jack had brought protection.



My bugs flooded into the facility, past the \emph{second }dismantled vault door.  The alarm was louder as I ascended the concrete stairs and made my way into the building.



The emergency lighting was on, casting the area in a red glow.  My bugs searched and scanned the area, in case any members of the Nine were lurking in wait.  So many ugly ways this could go.  So many threats that Jack could have on hand.  Cherish?  Screamer?  Nyx?  Ways to fool my senses, ways to shut me down or defeat me.  My only recourse was to get them before they got me.



\emph{Hey, passenger}, I thought.  \emph{Do me a favor.  If I get taken out of action and you step up to fight, work on taking out Jack, alright?}



My bugs stirred, moving further down the hall.  It was so far from a conscious direction that I wondered for a second if the passenger had listened.



No.  I'd tried hypnosis, I'd tried other things.  Some in Mrs. Yamada's office, other times in the PRT's labs, after dark, off the record.  Nothing brought the monster to the fore.



Just my subconscious.



\emph{Just.  }Like that wasn't something I couldn't help but wonder about.



But I'd made peace with it.  I couldn't barter with something that wouldn't talk back, but I could accept it, test and acknowledge my limits as far as they pertained to the entity that was apparently granting me my abilities.



I wouldn't turn away from it, wouldn't tell it to go away or hold back in my abilities.



My bugs marked the area, giving me the information I needed to navigate the facility.  It proved easier than I might have expected.  Rather than follow the winding corridors and make my way to the security checkpoints, I followed the path of casual destruction Siberian had left in her wake.  She'd knocked down walls to create the shortest possible route from the front doors to Ellisburg.



No casualties that I could detect.  No nonhuman life.



Had Dragon ordered this place evacuated before she was incapacitated, or had Nilbog gotten here first?



My bugs started to scan the area beyond the facility, inside Ellisburg.  They made it about ten feet before something like a frog's tongue began snatching them out of the air.



I withdrew the swarm back to myself, hiding my bugs beneath my cape and skirt, and I made my way through the opening into Ellisburg.



A goblin wonderland.  It was clear he'd altered it from its original layout, likely over the course of years.  The remodel had been more aesthetic than functional.  Floorboards had clearly been dug up and moved to the exteriors of the buildings, creating roofs and building additions that spiraled or twisted, with more boards propped up flat against the building faces on one side, painted or modeled in the same way the towns had been put together in old western movies.



The walls that surrounded Ellisburg had been painted as well.  To look from a distance, Nilbog's kingdom extended to every horizon, with crooked, impossible landscapes at the periphery of it, like an ocean frozen in time, grown over with grass and trees.  Oddly enough, they had painted the sky as an overcast one, where it was visible above the lush, unpredictable fields and forests.



Within the city, the trees had been immaculately cut and trimmed, and the shapes were just as strange; trees that were perfectly round, cubes, cones.  Where new trees were growing on lawns, as dense and close together as trees in an orchard might be, I could see heavy wires wound around them, guiding their growth into twists and curves.  The art of bonsai taken to a bigger scale, cultivating each tree in form.  Already, some of the largest ones were properly set up, meshing together with counterparts on the opposite sides of the street, forming lush, living wooden arches.



The grass had been cut, and I could see the attention to detail \emph{there}, even.  There were innumerable flowers growing across lawns, but the grass was neatly cut beneath and around them, as if someone had taken shears or scissors to the blades that grew between the flowers.  I couldn't make out any rhyme or rhythm in how the flowers or plants were laid out and how they grew.  It was an injection of color in the same way a random splash of paint from a palette might be applied to a canvas.



And then, as if to remind me that this wasn't friendly territory, there was a scarecrow in one garden.  The clothes were brightly colored, the pose one of a dancing figure, but that wasn't the eerie thing about it.  The head was a skeletal one, a dog's head stripped of all flesh, turned skyward with its mouth opened in joy.  The hands that clutched the rake and watering can were held together by wire.  A very small human hand.



For all the signs of careful tending, the entire place was still.  A town that could have been taken from a storybook, desolate.  There wasn't any sign of chaos, nor the destruction that would follow from an attack by the Slaughterhouse Nine.



But more than anything, what threw me was the absence of insect life.  No spiders spun webs.  Even the ground had little in the way of ants or earthworms.



\emph{A trap?}  I looked behind me to see if they were planning on walling me in, and came face to face with one of Nilbog's creations.



It hissed, its breath hot and reeking of bile.  Fangs like a viper's parted, the distance between them great enough that it probably could have sunk some into the top of my head and the underside of my chin as it closed its mouth.  I stepped back out of reach, then forced myself to stay still and wait.



The mouth closed, and I could see how the creature's head was smaller than mine.  It wasn't more than four feet tall, covered in pale brown scales.  The reptilian face could have been in a children's movie, if it wasn't for the eyes.  They were dark, black, and cold.



It clung to the wall, its feet placed higher up than its hands, opposable toes gripping the frame that had been around the vault door.  I noticed it was wearing white shorts, with one suspender strap over a shoulder.  A taloned claw held a softball-sized chunk of the wall.



\emph{Was it fixing the wall?}



``I'm not a threat,'' I told the lizard-child.



I felt hands touch my belt and jumped, seizing the wrist of the offending hand in an instinctive motion before I'd even looked to see who it was.



A girl, five or so feet tall, her face mottled with purple veins that spiraled across her perfectly round, puffy, hairless head.  Her eyes were tiny and piggish, her fingers blunt, barely a half-inch long, her mouth too small for her face.  She wore a sack that looked like it had been sewn to work around her oversized head.  Her hand was on my knife.



The lizard boy had extended frills at his arms, neck, and the edges of his face, colorful, brilliant, and held out by a framework of needle-fine spines.  His mouth hung open, viper's teeth revealed.



I looked beyond this pair, and I could see signs of others.  Eyes reflected light in the shadows beneath steps, from windows.  There were large, bulky silhouettes in the windows, some holding smaller figures on their heads and shoulders.  I couldn't make out much, but I wasn't sure I wanted to.



That was twice now that they'd snuck up on me.  Quiet motherfuckers.



``I'm sorry for grabbing you,'' I said.  ``You wanted my knife?''



She took it, her tiny black eyes glaring at me from the midst of her oversized head.  The lizard-boy eased his frills down somewhat, but his mouth remained open.



``I'd like to see Nilbog,'' I said.



She ignored me, her pudgy, blunt-fingered hands fumbling through the pouches at my belt.  With painful, clumsy slowness, she divested me of my taser, the pepper spray, and the spools of silk, both conventional and Darwin's spider silk.



I winced as one spool fell to the ground and unwound partially, dirt getting caught up between the strands.  That would be a pain to fix.



I could see more of the things making appearances now, getting close enough for me to see as they took interest in what was happening.  Eyes appeared in the windows, reflecting the light in curious ways.  Eyes from within the trees, between the slats of stairs\ldots some faces.  They ranged from artistic and beautiful to horrific.



Every single one of them was a weapon.  Going into this situation was a repeat of the information gathering and problem solving issues one faced when going up against an unknown cape.  If it came down to a fight, I'd have to figure out how they operated, and the full extent of their capabilities.



Trouble being that there were a hell of a lot of these things.  Hundreds, even thousands.



I waited patiently.  No use complaining, even if every second counted, and Jack was no doubt having words with Nilbog.



``Nilbog is in danger,'' I said, trying a different tack. ``The man with him, he has dark hair, a beard?  He's with a striped woman.  Bad people.  I think they're going to try to hurt Nilbog, hurt the man who made you, so you get upset and leave this place.''



Her hands fumbled with my flight pack.  I felt her touch the arm at the side of the pack, with its narrow arm.  She took hold of it and pulled.



``I can take that off,'' I said.



She grunted, and I started to move to oblige, only to get a protest.  The frills on the lizard boy extended, and her own head swelled, the skin getting thin enough in the process that I could see a fluid filling the lower half of her head.  I moved my arms away from the straps, and I watched them both relax over long seconds.



When she was sure I wasn't trying something, she grunted again, louder, a frustrated, constipated sound.  A communication, but not one meant for me.



Her \emph{friend} emerged from a garage, lifting the door to lumber forth.  He was big, fat, and moved on four limbs that each had opposable digits.  His massive belly swung right and left as he loped, so distended and so close to the ground as it swung that I worried it would hit something and split open. His genitals were almost bigger than I was, and they were, along with his sensory organs, the only way I could really tell his front from his back.



The sensory organs consisted of slits running top to bottom from a ridge at one end of his body.  There was no room for a brain, no eyes present.



This organ granted him enough awareness to approach, probably by way of scent, but it didn't give him the fine tuning he needed to find \emph{us}, specifically.  The round-headed creature approached him, took hold of a fistful of chest hair and led him my way.



I backed up a little as they approached, and received a hissed rebuke from lizard-boy.



I remained still.  The safest course.



The girl-thing moved the brute's hand towards me, and I stayed still as she gripped the arm and placed it in the hand.



He closed his fist around it.



``Wait,'' I said.



He hauled on it, clearly intent on tearing it free.  I was thrown, sent rolling until I landed in one patch of grass, dazed, startled, just a little hurt.



The brute approached, the round-headed girl hurrying after.



Before I could rise, he'd already fumbled for me, and seized hold of the mechanical arm.  This time, he managed to pull it free.  I used the antigravity panels to control my flight as I was thrown, controlled my landing, and hurried to get my hands to the straps.



There was a wail behind me, a warning sound.  I saw the others react, but kept working through the straps.  Two at the shoulders, one across the chest, beneath my armor-



The pack fell free.  I chanced a look over my shoulder, and I saw a number of Nilbog's creations gathered, close enough that they could have lunged for me.  One was a very tall, long-limbed man with skin that looked like a Siamese cat's, covered in a very fine fur.  His face was split by a wide, toothless mouth, his eye sockets little more than indents filled with fur.  He held a makeshift spear with a flag on the end, which had been painted brilliant colors, and wore a matching loin cloth.  Probably the most dangerous one in my immediate vicinity, just in terms of how fast he could probably close the gap and murder me.



``Safe,'' I said.  ``No danger.  I'm safe, the pack's off.''



I waited, tensed, as they studied me.  Enemies on all sides.



Jack was invincible, I wasn't.  But if I was going to achieve anything here, it couldn't involve destruction.  I'd read the files on Nilbog, I had a sense of him, in the most general terms.  I was banking everything on his megalomania overriding his desire to collect just a little more in the way of resources.



I kept my voice level and calm, ``I'd like to see Nilbog now.''



Were they hungry?  If this became a fight, I'd have to defend myself with the bugs in my costume and the bugs in the quarantine and filtration facility.  I could use the swarm to equip myself with the stuff that had been dumped on the ground, but that required that I survive long enough to do so.  Were there ranged attacks here?  Assassins?



Desperate situations called for risks.  This was my gamble.



``I have a gift for him,'' I said.



Something seemed to ease in them.  I watched as some turned away, finding their way to resting spots.  The tall man with the loincloth worked his overlong body under a porch, where he could rest in the shade.



I didn't receive an escort, but the ones along one road moved aside, sitting or standing on the sidewalks.



I walked with my head high, and sent a handful of bugs forward.  More than a few of Nilbog's creatures took the opportunity to snap them up.



A soft rumble sounded above.  Lightning.  Rain began to patter down, light.



My surviving bugs gave me ears on the scene before I arrived.



``Lipsy?  Tell the cook to serve us something.  I fancy a salad, and something \emph{robust}.  I think it should taste \emph{sweet}.''



The alterations to the surroundings only grew more focused and extreme as I found my way to the center of Ellisburg.  Building faces were covered in wild plant growth, and there wasn't a single building without more extreme modifications made to it.  Glances indoors showed little more than barren exteriors with the floorboards pried up, or clusters of Nilbog's creatures lurking in the unlit gloom within.



``I'll look forward to this, god-king.''



``You should, you \emph{should}.''



``Your hospitality astounds me.  I'm unworthy.''



``\emph{Hardly}.''



So Jack was situating himself as someone subservient, even \emph{servile}, so as not to challenge Nilbog's alpha status.  He was playing nice, even.



If I tried the same, I'd only be working to catch up, to earn Nilbog's trust.



I approached the town center, and found myself in the midst of a crowd of Nilbog's creatures.  Goblins and ghouls, muppets and horned moppets.  Big, small, thin and fat.  Each was exaggerated, \emph{twisted}, as if Nilbog had gone out of his way to insert traits and qualities that separated them from humanity.



The creatures stepped out of the way as I made my way closer.  Nilbog sat at the center of a long table, and two more tables extended from the ends to form a loose `c' shape.  Checked tablecloths in eye-gouging color contrasts covered each table.  Jack sat at the end furthest me, and a \emph{man} with white and black stripes sat beside him.



Bonesaw was only a short distance away, sitting on the shoulders of what looked like a flayed bear.  The thing had claws two or three times the usual size, it's mouth yawning open like it had been broken.



Nilbog was immensely fat, easily four hundred pounds, and sat on a throne that had apparently been cobbled together from dismantled furniture.  His face was covered with a paper mask.  Other creatures sat on chairs to his left and right.



The arrangement of the tables created an open space that could host their entertainment.  I looked, then wished I hadn't.  A bloated, coarse-looking creature lay on the ground, almost like a potato made of hair and flesh.  Smaller things were busy carving gouges and holes into it.



The resulting wounds regenerated, but not before the smaller creatures inserted body parts into the openings, allowing the regenerated flesh to close tight but not close \emph{completely}.



I averted my eyes from the scene, content with not letting my brain register which parts were being inserted and what they were doing after the fact.



``Another guest!'' Nilbog cried out.  He spoke like he had a bad accent, but it wasn't.  He'd affected strange and overdramatic tones for so long that his voice had warped, and he'd had no ordinary people to hear or talk to and measure his voice against.  ``A friend of yours, sir Jack?''



I could see Jack's eyebrows raise in interest.  ``Not at all.  Skitter, was it?  Except you're going by another name, now.''



I ignored Jack.  ``Nilbog.  It's good to meet.''



Nilbog didn't look impressed.  ``Sir Jack was more \emph{obsequious} when he introduced himself.''



``That's because he's a two-bit thug, Nilbog.''



Jack chuckled at that.



``A two-bit thug?  You'd insult my guests?''



``If those guests include Jack,'' I said.



Nilbog narrowed his eyes.  ``I will not have fighting in my glorious kingdom.  Jack has agreed to a ceasefire while we dine.  You will do the same.''



``I already gave my weapons to your underlings.  You should know that the black and white striped man is a living weapon, much like your creations.''



Nilbog glanced at the male Siberian.  ``I'm not concerned.''



``I imagine you aren't,'' I said.  \emph{Where's the real him?}



I had to be careful in how I used my bugs.  Sending them into buildings would only reduce the size of my swarm, but there was relatively little chance that Manton would simply be hanging out in one of the hollowed-out buildings.



``So,'' Jack said.  ``Are you going to have a seat, or are you going to continue to be \emph{rude}?''



``I'm waiting for our host to invite me to sit.  Forgive me, Nilbog,'' I said.  I glanced at the fat man.  The grease on his skin made it look like he'd \emph{oiled} himself.



``Sit.  But I'd like to hear who you \emph{think} you are, whelp, if you won't bow down to me.''



I approached the row of chairs opposite Jack and the Siberian, and one of the critters hopped down, scurrying under to join the \emph{festivities} in the center of the tables.  I took the vacated chair and sat.  I might have removed my mask, but I was all too aware of the silverware in front of Jack.



``I'm your equal, Nilbog.''



Jack laughed again.  Nilbog seemed to react, almost looking flustered, before turning to me.  ``You \emph{insult} me.''



``Not at all.  Ignore the thug that's sitting over there.  I'm a queen, a goddess of my own realm.  Or I \emph{wa}\emph{s}.''



Jack was smiling, clearly amused.  Then again, he was safe.  He was untouchable with Siberian beside him, and he was only feigning weakness to get past Nilbog's defenses.



``A queen?''



``A queen.  With that in mind, provided you give your permission, I'd like to offer you a gift.  A\ldots peace offering, to make up for the fact that I entered your territory uninvited.''



``Of course, of course!''  He was almost childlike, so easily moved by this promise of a gift, his mood changing so quickly.  \emph{Guileless}.  He'd been surrounded by yes-men for more than a decade, with barely any human contact, his defenses were gone.  ``I forgave Jack the lack of an invitation, I'll extend you the same courtesy.  This gift?''



I called on the swarm I'd kept within the quarantine facility.  ``Resources are slim.  An isolated kingdom like yours, providing for your subjects is hard.  You do an admirable job despite this.''



``Of course, of course.''



He was eager, impatient.



``I'd feed your subjects,'' I said.  ``Protein.  You need it to make \emph{more}.  To keep the ones you currently have in good health.''



``Yes, yes'' Nilbog said.  My bugs were just now arriving in the area.  ``This will do.''



The full swarm arrived, the vast majority of the ones I'd kept in the Dragonfly, and the ones from the area beyond the Ellisburg walls.  I gathered them on plates in piles.  His minions devoured them, licking at the plates, picking with talons, or simply lifting the plates and tipping the insects into open mouths.



I wasn't surprised when Nilbog turned his attention to his own plate.  My eyes fell on Jack.  He still had a slight smile on his face.



He held the cards up his sleeve.  I'd played mine for a minor advantage, but he had Bonesaw.  One virus or parasite in the midst of these creatures, and they could go berserk, roaming the countryside until they were put down.  He had Siberian, which meant he was \emph{safe}, meant he could kill me or Nilbog whenever he wanted.



But he wasn't going to.  This continued as long as the game was still on.  He thrived on this interplay.



As more bugs continued to arrive, I used them to search the area.  Nothing.



Below ground?



Earthworms, ants and pillbugs dug through the soil beneath the park, searching.  Some of Nilbog's creatures were beneath the earth, ready to spring up and attack.  Others were beneath, eating whatever they could find.



In the midst of my search, I found something.  Not Siberian's creator, but nearly as good.



Nilbog himself.



He sat directly beneath his `throne', and was connected to the fat man by what seemed to be an umbilical cord.  This cord gave him control of the body, fed him sustenance, let him stay safe while the decoy sat up here.



One card for me to play.



``I think the bug queen here should explain how she came to nobility,'' Jack said.



\emph{Setting me up to say something incriminating}, I thought.  ``As you did, Nilbog, I claimed a realm for myself.''



``And you left it, apparently.  If you're truly a queen, you're a foolish one.''



``I did leave it,'' I said, ``Because I had to, to save it.  I had to protect my subjects, to fight my people's enemies.  I have not been as fortunate as you.''



``No,'' he said, uncaring.  ``Apparently not.''



``If it came down to it, would you step up to protect your creations?  To protect this town you made?''



``You're sounding a great deal like sir Jack,'' Nilbog commented.  He frowned.



``He's trying to convince you to go to war,'' I said.



``To take \emph{pre-emptive} action,'' Jack clarified.



``I'll do neither.  Not war, not pre-emptive action.  I have what I need.  I'm a content god, a happy king.''



\emph{You're starved for real human contact}, I thought.  \emph{Or you wouldn't have let us join you at the table}.



My bugs continued to search, though the bastard creatures were coming out of the woodwork to catch and devour them.



Where in the hell was Manton?



Jack spoke, ``It's a question of whether you act now and preserve what you have for the future, or wait and let them come and kill you.  They've been systematically seeking people like you, eliminating them.  I could show you proof, given a chance.''



``I'll make it simpler,'' I said.  ``You \emph{don't} need to leave your kingdom, your garden.  You \emph{don't} need to go to war with an outside party you don't know or care about.  You want to know what happened to my kingdom?  That man, right over there, \emph{sir} Jack, destroyed it.''



``Nonsense,'' Jack said.  ``I've been sleeping these past few years.  Naps are such an underrated pleasure.''



``They \emph{are},'' Nilbog said.  ``All of my subjects nap every day.''



``Let me explain,'' I said.  ``I had a kingdom that I ruled.  I had a king that ruled with me, who kept me company.  I had wealth, people I cared about, people who cared about me.  Power.  I was a god in my domain, and those who stood against me were driven off.''



Nilbog shook his head.  ``You need a heavier hand to rule.  More loyal subjects, so you don't have to bother with those who would stand in your way.''



``I was more powerful than you,'' I told him.



He snapped his head around to stare at me.  To \emph{glare} at me.



I'd pricked his pride, apparently.



``I was more powerful than you, but Jack over there made a promise to people.  He didn't say it aloud, but it was still a big promise.''



``Now you're making stuff up,'' Bonesaw commented.  She slid down off the flayed bear's back and joined a group of creatures her size.  She hugged one, abruptly.



But Nilbog wasn't telling me to fuck off.  His attention was on me.



He'd built a storybook kingdom, an impossible place, and populated it with monsters, both beautiful and ugly.  He'd had some fixation on this stuff, some Freudian obsession.  Not \emph{sexual, }but still rooted in some primal part of his childhood that had been taken from him.



I'd play this by telling him a fairy tale.



``No,'' I said.  ``And I think Nilbog is clever enough to understand what I mean.  Jack promised that he'd come back when his nap was done, and he'd destroy my kingdom.  He said he'd destroy \emph{your }kingdom, Nilbog, and every other kingdom.  He said he'd kill all of my people, and he'd kill all of \emph{your} creations.''



``All of this, from the man you describe as a mere thug?''



``Yes,'' I said.  ``A woman with great powers told him he could do it, and now he's going to try.  It's why he's here.''



``To destroy my kingdom?''



``No.  He wants you to go to war against your neighbors.  To break down the walls that keep you safe and fight people who are leaving you alone.  He'll use you as a distraction, and then when everything is done, he'll come back and destroy your kingdom.  And he'll do it in the cruelest, saddest ways you can imagine.''



Nilbog nodded slowly.



Jack was still waiting patiently.  Too quiet.  I felt a moment's trepidation.  I hadn't found Siberian's controller.  I needed to defeat him before Jack was cornered.  The second he decided he couldn't salvage this situation, he'd order the attack.



Nilbog raised his hands.  ``Angel on one shoulder that tells me one story\ldots''



A placenta-like blob swelled in his hand.



``A devil on the other, telling me another.''



Another blob appeared in the other hand.



Both burst, showering Nilbog in greasy slime.  Two creatures gripped his forearms, looking more like flying monkeys than an angel and devil.  They were roughly the size of babies, their faces feral, mouths filled with pirahna-like teeth.  One had red hair, a red beard and gazelle-like horns, and the other had white hair and beard and a strange horn that formed an off-white halo above its head.



``I'll take the angel, if you please,'' Jack said.



Nilbog shrugged.  Were the creatures more a demonstration than anything else?  He lowered his hands, and nudged the white-haired thing in Jack's direction.  The other thing made its way to me.  I reached out and took it into my hands, holding it close.



``Do you have a response to the Queen's allegations, \emph{Jack}?''  Nilbog asked.  He reached up to adjust his floppy cloth crown.  Creatures were arriving to deposit the meal on the plates.  It looked like purple vomit.



``I do,'' Jack said, smiling.  ``But can we eat first?  It's rude to argue over a meal.''



Nilbog nodded, as if Jack had said something very sage.  ``I agree.  We'll eat.''



Bonesaw made her way to the table.  ``How did you make this?''



``The chef stores every ingredient we can find inside her, then regurgitates it in the form required.  I asked for it to be hearty, and here we have it, chunky.''



I looked down at the plate.  Droplets of rain made nearly-clear spots appear in the midst of the purple slop.



\emph{So it is vomit}.



``It tastes like cupcakes,'' Bonesaw said, around a mouthful.



I started to move my mask to eat and be polite, then noted how Jack was holding his knife.  The blade swayed back and forth in the air, as he chewed, his eyes rolled back and looking up at the overcast sky above.



The blade was making criss-crosses in the direction of my throat.



He glanced down, meeting my eyes, and smiled.



``Our apparent rivalry aside, have you been well, bug queen?''



``Well enough.''



``Then you should be hungry.  It's been a \emph{busy} few days, and it'll only get more interesting.  I notice your friends are sitting this one out.  Did you break it off completely, or are you still in touch?''



``Still in touch,'' I responded.  I glanced at Siberian.  \emph{The knife is a purely psychological thing.  If he wanted to kill me, he could use Siberian to do it.}



Besides, it was a butter knife.



I moved my mask, without breaking eye contact with Jack, and helped myself to a bite.



It \emph{did} taste like cupcakes.  I suspected it would have been less nauseating if it tasted like real vomit.



It was a tense few minutes of silence as we ate.  I found out the devil-thing in my arms wanted to eat, so I let him help himself.  An excuse not to eat, anyways.



The creatures in the center of the area finished their `show', and Nilbog clapped enthusiastically.   I joined him and the five or six creatures around the table who really had \emph{hands} to clap with.



The second show began.  A gladiatorial fight, apparently.  One of the creatures had wings instead of arms, while the other had wicked barbs extending out from the elbows and knees.  When even the tips made contact, they ripped out grapefruit-sized chunks of flesh.



I braced against the table to keep it from flipping as the pair crashed into it.  Nilbog laughed, and the sound was more than a little unhinged.



``Is everyone done?'' Jack asked.



``Yes,'' Nilbog decided.



``Then let me explain.  Weaver's entirely right.  Except for the part where you die at the end of it all.''



``Oh?'' Nilbog asked.  He leaned forward, placing fat elbows on the table's surface.  It dipped as his upper body weight rested on the wood.



``Living like this, you obviously dislike the system.  You \emph{know} how screwed up things are out there.  People are vile, self-centered, and so caught up in their own routines and expectations that they're barely \emph{people} anymore.  Your creations have more personality.''



Nilbog nodded, taking it all in.  ``They do.  They're wonderful, aren't they?''



``\emph{Wonderful},'' Bonesaw agreed, with the utmost enthusiasm.



\emph{He just believes whatever we tell him.  He's a sponge.  How do you convince someone who's so incapable of critical thought}?



Worse, Jack was touching on all of Nilbog's pet issues.  The man had been a loner before, a loser.  He'd rejected the trappings of society \emph{long} before he'd become this monster.  He'd spent years simply going through the motions until the last parts of the system he'd clung to fell apart.



``I want to wipe the slate clean.  Things have been going through the same motions for so long that there's a \emph{rut} in the ground.  You erased everything that wasn't worth keeping here, and replaced it with something \emph{better}.  With your \emph{garden}.''



``Yes.''



``With that in mind, I'm reaching out to a like-minded soul.  Someone who rejects the malignant, \emph{stagnant} society and wants to grow something else in its place.''



``Jack has no interest in growth,'' I said.  ``Only destruction.''



``Did \emph{I} interrupt \emph{you} when you were speaking?'' Jack asked.



``Do it again and I'll order your execution,'' Nilbog said.



I pursed my lips behind my mask.



Where the \emph{fuck} was Siberian's creator?  I'd scanned every area where he could be lurking.  There were only monsters.  I was nearly out of bugs.  I had only a select few secreted away in my armor, and they weren't ones I was willing to sacrifice.



I didn't have much in the way of cards up my sleeve, but these bugs would have to serve in that department.  Problem was, they wouldn't fix anything \emph{now}.  Bonesaw could counter them too readily.



Where could Manton be hiding?  My eyes passed over the crowd of creatures that had gathered around the edges of the area, enjoying their master's presence.



\emph{Hiding in plain sight}.



Plastic surgery, or even an outer suit, like the one Nilbog wore.  He had to be dressed up in the skin of one of the monsters.



\emph{Shit}.  How was I even supposed to assassinate him if he was going that route?  I touched him with a bug, only to find his flesh harder than steel.  Unmovable, just from the way his foot touched the Siberian's.



Jack licked his plate, then set it down on the table.  ``Where was I?''



``Replacing society,'' Bonesaw volunteered.



``\emph{Replacing society},'' Jack affirmed.  ``Imagine if your garden really did extend as far as the eye could reach.  If you could walk in the direction of the sunset, only to find that your creations have already settled in each new place you travel to, decorated it, \emph{transformed} it.''



``A romantic goal, one I might pursue if I were a younger man,'' Nilbog said.  ``But even gods get older.''



``They do,'' Jack agreed.  ``Well, we could give you that youth.  Bonesaw could grant you immortality.''



``She could also enslave you to her will,'' I commented.



``I'd \emph{never},'' Bonesaw said.  She shook her head, her curls flying, ``No, I couldn't!  I love these beautiful things he makes!  To control him would mean I'd take that creativity away.''



Nilbog nodded at that.  ``That's a good argument.  Besides, to enslave a \emph{god}?  Madness.''



\emph{Except they're mad}, I thought.  \emph{All of you are lunatics, and I made the mistake of trying to talk sense}.



``It's a good argument,'' Jack said.  ``Because we're \emph{right}.  Would you like to live forever, as a god should?  Would you like to see your garden grow to what it should be?  What it \emph{deserves} to be?  Something fitting of a god?''



``It's a tempting thought,'' Nilbog said.



I reached for a rebuttal, telling myself I had to be just as grandiose, just as \emph{mad}, but I couldn't do that at the same time I was trying to convince him to go \emph{dormant} again.



``If I may?''



It was another human voice, but it didn't belong to any of us.



Golem.



He approached, taking off his helmet.  He offered Nilbog a slight bow.



``One of yours, Jack?'' Nilbog asked.



``No.  Not in the sense you mean.''



``Yours, then?'' Nilbog asked me.



\emph{Yes}, I thought.



``No,'' I said.



I saw Jack raise his eyebrows at that.



``Shenanigans!'' Bonesaw cried out.  ``I call shenanigans!''



But Golem took my cue.  ``I'm a third party.  I stand for myself.''



``Hardly worth a place at the table,'' Jack commented.



``Then let me stand for the others.  The innocents.''



``Innocents?'' Jack asked.  He snorted.  ``No such thing.''



``There's always innocents.''



Jack smirked.



``I'll allow it,'' Nilbog said.  ``Excellent!  Sit!  We were just having a discussion.''



Golem approached and sat at the same table I was at, but he took the far end.  ``I've overheard some, so we can cut straight to the chase.''



``The dilemma,'' Nilbog said.  ``The devil on one shoulder, the angel on the other.''



``The sin of sloth versus the realm of \emph{possibility},'' Jack added, gesturing to my demon as he said sloth, then to his own angel.



``Well said, well said!'' Nilbog said.  He nodded so hard his double and triple chins wobbled.



``Or is the \emph{angel} making false promises?'' I asked.  ``There's no security.  No comfort.  You claim to care about your creations, but you'd go to \emph{war}?''



``Many have gone to war and made sacrifices in the present, for the sake of a brighter future,'' Jack commented.



``I thought you were trying to break \emph{out} of the rut?'' I asked.



Jack laughed at that.



\emph{He's enjoying this}.



I felt almost dirty, knowing I was only helping Jack in his self-indulgence, helping him revel in conflict.



``Well, stranger?'' Nilbog asked.



``Golem,'' Golem said.



Jack snorted at that.  He'd caught the meaning behind the name right off, the white supremacist's son naming himself after a creature from a Jewish parable.



``Golem, then.''



``I'm not an eloquent speaker.''



``That's a good thing,'' I said.  ``Too many and it just becomes people talking circles around one another.''



``Then I guess I have to get to the heart of it all.  Direct.''



``Yes,'' Nilbog said.  He leaned forward, and I feared the table would break.



``Were you happy, before any of us came here?''



``Yes.  I can eat the most delicious foods, yet get every nutrient I need.  I can \emph{fuck }the most beautiful and exotic women you'd ever imagine, whenever I wish.  Every need is provided for a hundred times over, and I'm surrounded by those who love me.''



``Then why change?  Why do anything?  Let us leave, then return to your utopia.''



Nilbog nodded.  He rubbed at his chin, but the act was like pushing one's hand into jello.  It shifted the mass more than it \emph{rubbed}.



``You wanted a tie breaker?'' Golem asked.  ``This is it.  Do what Weaver is saying.  Do what the Queen is suggesting.  Stay quiet, enjoy what you've built here.  Attack, and the entire world will take it away.  Then, even if you're strong enough to survive that, which you may be, then Jack will still betray you.''



``Or,'' Jack said, ``You can stop lying to yourself.''



Nilbog snapped his head around.  He growled, ``\emph{Impertinent}.''



``Your people are slowly starving.  You make them eat each other to live, and desperately attempt to shoot any birds out of the sky so you can try to recoup what you lose.  Bonesaw said they don't live long.  How long?''



``Four years.  Sometimes five.''  All at once, the light was gone from Nilbog's face, the sudden fury quenched.



``Who's your favorite?'' Jack asked.



``Polka,'' Nilbog said.  He reached out, and a female creature, no taller than three feet, hopped up onto the lap of the creature beside her king.  She had a narrow face with a reptilian structure, with only four fangs at the very front, but smooth, humanlike skin.  Her hair was white, her skin blue.  She wore a toddler's clothes, a long, narrow tail lashing behind her.  Nilbog stroked her hair.



``Not the first Polka,'' Jack said.



``No.  The third.''



``She was your first, and you love her for that, because she drew you from the hell that was your life before godhood, gave you \emph{this}.''



\emph{I can't interrupt this.  Not with the subject being something so close to Nilbog's heart.  I might win the argument, but I'd lose Nilbog's ear}.



But I knew I was losing anyways.  Jack had found Nilbog's weak point.



``My first friend,'' Nilbog said.



``And she dies.  Because your creations don't last.  You make another, and slowly fall in love with her all over again, and yet you know she'll die in turn.''



``Yes,'' Nilbog said.



``Bonesaw can fix that.  I can grant you immortality.  I can grant your creation that same gift,'' Jack said.



``A hard offer to refuse.''



``It would be wise to refuse,'' Golem said.



``A king can't be selfish,'' I said.  ``A god \emph{definitely} can't be selfish.  Your responsibility is to your creations.''



``Exactly what I'm saying,'' Jack said.  ``Step out of your comfort zone, to better your people.''



``Enough!''  Nilbog screamed the word.  As if responding to his anger, every single creature in the area responded.  Weapons raised, spines extended.



And Jack was still invincible.



``Nilbog,'' I said.



``Speak again, and I'll end you, queen or no.''



His eyes were angry, hard.



He'd lived for so long in his comfort zone, and now he was being called on to make a hard choice.



``Then please listen carefully,'' I said.  ``Because I suppose I'm paying for this with my life.''



``So be it,'' he said.



``If you want proof that Jack intends to betray you, look no farther than your own creations.''



``What?''



``He's secreted an assassin into your midst.  A killer who pretends to be one of your creations.''



\emph{A gamble, a last ditch effort.  }Was my gut right?  Had Jack instructed Bonesaw to create a costume or a creature to hide the Siberian's creator?



I called my flight pack to me, parked it on a rooftop nearby.  If it came down to it, I'd have to run.  I could see Golem tensing.  He'd read the situation right.



``Just look,'' I told Nilbog.  ``Because somewhere nearby, there's a creature you \emph{didn't} create.''



His eyes roved over the crowd.



``Might not be in \emph{this} crowd, but it'll be close.''



``I see it,'' Nilbog said.  ``I see it.  Bossy, Patch, hold him!''



The crowd of creatures parted as two creatures took another in their hands.



``Not an assassin,'' Jack said.  ``Merely one of Bonesaw's\ldots I suppose you can call it a \emph{homage}.''



``It is,'' Bonesaw said.



The Siberian was moving.  Readying to pounce?



I couldn't move fast enough if he did.



``Wait,'' Jack said.  He stood from his chair.



\emph{No}, I thought.  ``Don't listen.''



``I'll do as I please,'' Nilbog said.  ``Last words, sir Jack?''



``Last words, yes.''  Jack approached the captive.  The Siberian followed.



``You let him do this, and he kills you,'' I said.  ``Your creations will go mad with grief, and they'll die in a war for vengeance, \emph{just like Jack wants}.''



``Not at all,'' Jack said.  ``Because\ldots''



An instant before the Siberian made contact with the monster, Golem jammed his hand into his side, using his power, throwing the creator into the air with one thrusting hand.  Siberian lunged, punching through the hand of soil to grab the creator's foot.



Nilbog half-rose from his seat, though he was massive enough that standing was hardly possible.  His eyes moved from Golem to the hand, anger etching his expression, if one could \emph{etch} into a face as soft as his.



``You \emph{dare} disturb the peace!?'' Nilbog screamed the question. ``Kill the queen!  Kill the Golem-man!''



In that instant, Golem created two hands, throwing us back.



I caught the flight pack in the air, hugging it.  It provided lift.  Not enough to stop my momentum as I headed back towards the ground, but enough that I could shift my direction to land on a rooftop.  Golem wasn't so lucky, as he fell into the midst of a sea of the creatures.



``Azazels, \emph{now!}'' I screamed, one finger pressed to my earbud.  I pulled on the flight pack and then took off again.



Golem used his power to create a platform, slowly raising himself above the street.  Creatures tumbled off of the surface of it.  Some flew at him, and he struck at them.  Not enemies he was capable against.  I sent my bugs to them, the reserve I still had on hand, commanding the bugs to bite and sting.



Others leaped onto rooftops, then onto the rising platform.  Golem grabbed one claw as it slashed for his face.  He couldn't do anything about the other, as it gouged his armor, scoring it.  He created a fist that jutted out of his chestplate, striking the creature off of the rising hand-platform.



Spines rained down on him.  One caught him in the shoulder, and he collapsed.



``\emph{Where are the Azazels!}'' I shouted.  The flying creatures were turning my way.



But Defiant had said they were unreliable.  Dragon was out of commission.



My bugs burrowed towards the buried Nilbog.  Jack had orchestrated a war.  Killing the creature's creator wouldn't stop that, wouldn't keep them from rampaging and seeking out revenge beyond the walls.



But it would slow things down.



They inched ever closer.  Jack was untouchable, but\ldots



Yes.  Worms, centipedes and other subterranean bugs made their way to the buried goblin king, and forced their way into the sac that enveloped him, past the threads of material that wound down his throat and nostrils, and into his airways.



``Creatures of Ellisburg!'' I screamed.



Heads turned.



``You've been betray-''



And before I could say more, Jack's knife slash caught me across the chest, the cut severing the straps of my flight pack.  I dropped from the sky, landing on one of those ramshackle, spiraling rooftops.  Planks that had been poorly nailed in collapsed around me as I hit solid ground.



My hope of turning the monsters against the Nine had been foiled.  The fall had knocked the wind out of me.  I couldn't get my footing, and the creatures were advancing.  Every possible combination of features, it seemed like, an infinite army, unpredictable.



\emph{Your king is dying}, I thought, my mouth moving and failing to form the sounds.  There was only the barest whisper.  \emph{I killed him, but if you could believe that Jack did it}\ldots



I would have used my bugs instead, but I had so few, here.



I sent those few to Golem, removing them from the flying creatures.



``\emph{Nilbog dies},'' I spoke through the bugs, but the range of sounds was too limited, and with scarcely thirty bugs in total, they were quiet.



``\emph{Nilbog's dying},'' Golem said, his voice coming through the comm system.



One creature, eyeless, like a crocodile with a serpentine body, advanced on me, looming over me.  Its jaws opened.



The lizard boy was here too.  A drop of venom appeared on one distended fang.  I was surprised by the fury on his expression.



``\emph{Blame Jack},'' I said, through the swarm.



``Jack Slash has used us as a distraction to kill your king!''



Golem hollered the words at the top of his lungs.  I felt a tension leave me.  I might be \emph{fucked}, but we'd limited the damage.  They'd turn it inward.



The attack stopped.  The creature looming over me turned and slid away in a flash.  The lizard-boy remained.  Still recovering from the fall, I couldn't muster enough strength to fight back if he bit.



I commanded the flight pack instead, flying it into him with both wings extended.  He was brained, and the pack ricocheted off his skull, one wing shattering.



Golem had risen almost to safety, though he was still too far from the wall that had been erected around the city.



I looked at the wall.



Looked past it, at the capes who were swiftly approaching.



Rescue.



I brought the flight pack to me, the broken wing partially retracted, the other still extended, and pulled it on with slow, agonized movements.



Lost without their master, half of the creatures seemed to turn on the Nine, the other half seemed to remain intent on Golem and me.



Capes settled around me, forming a defensive line against the ones who approached.  Revel was among them, using her energy blasts to pick off the largest ones.



Someone picked me up, then took flight.



``\emph{Jack},'' I wheezed out the word.



The Siberian took hold of the umbilical cord and \emph{heaved}, Jack maintaining contact with a hand on the Siberian's shoulder.  Nilbog, still slowly dying of oxygen loss, was brought to the surface with a surprising ease.  Bonesaw wrapped her arms around the man.  Frailer than his self on the surface, \emph{smaller}.



I felt a moment's despair.



Foil?  Someone who could stop Siberian?



\emph{Somebody?}



The heroes advanced, but the Nine created a portal, and were gone in a flash, Nilbog carried between them.



Leaving the monsters of Ellisburg to riot.





