





Unholy screams and screeches followed us as we made our retreat, landing beyond the walls of Ellisburg.  In moments, Nilbog's fairy wonderland had become a hell on earth, thousands of demons crawling from the literal woodwork to attack.  The ground split as subterranean creatures emerged, while others climbed out of buildings that seemed to have been built around them.  One was somewhere between a dragon and a gargoyle in appearance.  Big, leathery wings, with a gnarled body and a leering, fanged face.



The flying creatures, the gargoyle-dragon included, took flight perching atop the walls, then backed down as a barrage of gunfire and superpowered attacks assaulted them.



``Shuffle!'' Revel cried out her lieutenant's name.



Shuffle stepped forward and used his power.  Teleportation, but not teleportation of living things.  Not \emph{people}, anyways.  Grass didn't hinder him much.



He teleported the \emph{landscape}.  A hill was bisected and placed against the ruined entrance of the facility.



His power was unpredictable.  There were metrics he couldn't quite grasp or understand.  Teleporting things \emph{in} sometimes teleported things \emph{out}.  In attempting to shore up the wall, he created gaps.



But this was a known issue, one he'd been dealing with for some time.  Unsurprised, he fixed the resulting hole with two more followup teleports.  If any terrain was removed, it was inside the structure, unimportant.



Something inside Goblintown struck the wall, hard, and then started clawing at it.  I could sense it's silhouette with the few bugs I had near the area.  It was four-legged, with all of the most effective parts of a rhino, bear and elephant combined, and it was big enough that I suspected it could make its way through the great concrete wall.



Defending capes had gathered in a loose ring around Ellisburg.  Revel and Shuffle were among them, which I took to be a sign that Golem's group had handled whatever issues had arisen in Norfolk.  The heroes opened fire as the gargoyle-dragon thing explored the upper edge of the wall again, and it disappeared, only to make an appearance further down, trying to find a spot where the defensive line was weaker.



This was the worst case scenario, on so many levels.  We couldn't afford to be dealing with this.



``Two more attacks,'' Revel said.  ``Just minutes ago.  Two different cities.  The situation in Redfield is still ongoing, which means we have three crisis situations set up by the Slaughterhouse Nine.''



``Four, if you count this,'' Shuffle said.



The creature hit the wall again.  Shuffle shored it up, placing the other half of the hill against it.



``This is getting out of control,'' Revel said.



``You're implying we \emph{had} control,'' Jouster said.  He stood off to one side, with the defensive line of capes.



``\emph{More} out of control,'' she said.



I'd been placed on the ground as the capes landed.  I was aware that someone was checking me for injuries, but it seemed secondary.  I stared up at the overcast sky, watching the rare raindrop tap the lens of my mask.  My mind was whirling while my swarm was feeding me information on the ongoing fight, both inside and outside the walls.



I stirred as I heard Golem's voice.  He was sitting a short distance from me.  ``This is my fault.''



``It was a lose-lose situation,'' I said.  I moved my arm to allow the medic to check my ribs.  ``Jack set it up this way.''



``I could have done something.  Said something different.''



``No.  We played the cards we had available, it wasn't enough.  Bonesaw's power and Siberian's invulnerability made for ugly trump cards.''



``There had to be a way.''



``We're coping,'' I said.



``Are we?'' he asked.  ``It doesn't feel like it.''



``We came through every challenge he set in front of us so far.''



``That doesn't mean we're doing okay,'' he responded.



I didn't have a response to that.



He stood.  ``I'm going to go talk to some of the people in charge, find out where I can be useful.''



``Okay,'' I told him.



He walked off, and I let my head rest against the ground.



Jack had a game plan here, and the more I thought about it, the more the `game' seemed to be a farce.  He \emph{knew} we were helping.  He was setting up situations where we \emph{had} to help.  When we'd started winning, maybe even winning faster than he'd anticipated, he'd ratcheted things up.



Just as it had at the outset, the situation now seemed to offer Theo the same dilemma as Jack had aimed to provide early on.  To go after Jack or focus on bigger things.



It was measured, calculated, and it suggested that Jack was fully aware and fully in control of what was going on.



A cape knelt beside me.  ``Are you alright?''



We'd only gone through a small fraction of the Nine.  Even assuming every group we had run into had been exterminated, there were \emph{so many} left to deal with.



My strengths lay in problem solving.  Jack's strength lay in problem \emph{creation}.



We came up with a solution to whatever crisis he posed, he responded by creating another, something offbeat enough that we had to change things up.  Specialized groups of his pet monsters, two scenarios at once, and now we had new issues popping up before we'd \emph{finished }with the last round.



The clones weren't as fleshed out as the originals.  A little more reckless.  They were being set up to fail.  Were they scary?  Yes.  Were they effective?  Yes.  But we were winning, and Jack wasn't using them in a way that kept them alive.  They were expendable assets.



It was all too possible that we could keep winning, if the game continued down this road.  \emph{We'll lose some, but we'll come out ah-}



\emph{No.}



\emph{Golem was right.  We'd achieve a steady stream of victories}.  \emph{Nothing more}.



``Weaver?''



I pushed myself to my feet.  A cape put his hands on my shoulders, to try to get me to stay still.



``I'm fine,'' I said.  ``I got the wind knocked out of me.''



``If you have an injury--''



``I'm pretty experienced when it comes to being injured.  I'm fine.  Really,'' I said.



He didn't move, but he did let his arms drop from my shoulders when I pushed them off me.  I found my feet, straightened, and felt aches all across my back where I'd collided with the ground.  I'd be one giant bruise tomorrow.



Then again, if we \emph{saw} tomorrow, it would be a bonus.



The fighting against Nilbog's creations was still ongoing.  The flying gargoyle-thing had made it over the wall and was being swarmed by defending capes.  Others were just now starting to climb over, and did their best to avoid the ranged fire that pelted them.  Eight or nine more creatures flew over, only these ones carried smaller `goblins'.  The winged ones were shot out of the sky, but many of the smaller creatures managed to survive the fall into trees and the midst of the heroes.   The ones that did went on the offensive with zero hesitation.



``Need the Azazels!'' someone shouted.



I directed the few bugs I had in the area to attack, assisting with bites, stings and silk cord.



I would help, but I wouldn't join the battle.  Not this one.



No, I'd used up every bug in my reach, and the damned goblin-things were too good at killing them.  Nilbog had no doubt designed them to live off of a diet of insects, to supplement their diminishing supply of protein.



I made my way to the Dragonfly, my flight pack dangling from the damaged straps I'd looped around my shoulders.



I'd very nearly told myself that we were coming out ahead.  Golem had been a dose of reality on that front.  We \emph{weren't }coming out ahead.  Jack was spreading fear, he was killing innocents, and he was whittling us down.  Doing so with such expendable forces cost him nothing.  Now, with Nilbog in his possession, he had access to that many more monsters and freaks that he could just throw away.



There was no guarantee we would continue down this road unfettered.  Just the opposite.  I fully expected Jack to turn to the rules he'd established at the very beginning and state how blatantly we were cheating.  Then he'd carry out his threat, murder those one thousand people, and move on.



I reached the console, shrugged out of my flight pack and sat down.



I pressed a button, ``Defiant.  Not a priority, but get in touch when you can.''



It took a minute before I had all of the individual windows open.  I set it so I could track the feeds provided by the various members of the Wards and Protectorate.  Some were here, others were investigating the sites where more members of the Nine were taking action.



Redfield.  The Undersiders and Brockton Bay Wards were holding a defensive position, their backs facing one another.  Foil took a shot at a flesh toned blob that leaped between rooftops, then swiftly reloaded.  Skinslip.



Skinslip was a minor regenerator with a changer ability, allowing him to manipulate his own skin.  I could see him using it to scale a surface.  He extended that ability by flaying people and crudely stitching or stapling their skin to his own.  The regeneration connected the tissues and extended his power's breadth and reach, but it didn't prevent all rejection or decay, forcing him to replenish it from time to time.  He was a newer member, but they'd still cloned him.



A quick check of the computer noted the members of the Nine they'd seen and fought.  Three Skinslips.  Three Hatchet Faces.  Three Miasmas.  Three Murder Rats.



Hatchet face excepted, they were enemies who were exceedingly mobile.  Skinslip's skin acted like a grappling hook, it let him climb, and it broke any fall.  He could also smother and bludgeon his opponents with it, if he felt the need.



Miasma was a stranger, invisible and undetectable but for an odorless gas he gave off that wore away at other's minds, causing headaches, ringing in the ears, watery eyes and eventual blindness, memory loss and coma.



Murder Rat, for her part, was agile.



It meant they were up against nine opponents that were fast or slippery enough that they couldn't be caught.  That group was supported by a trio of Hatchet Faces that could steadily lumber towards the group, keeping them moving, ensuring they couldn't simply maintain a defensive position.



The camera images that Clockblocker and company wore shifted as they scrambled away.  There was a shudder as a mass landed in their midst.



Hatchet Face, dropping down from a vantage point somewhere above them.



Rachel's dogs went on the offensive, attacking him, but their flesh was already sloughing off, their connection to Rachel shut off, their bodies disintegrating.



Parian's creations were already deflating.



More range than the Tyrant had possessed, and the power loss was immediate.



Foil shot her crossbow, but it did surprisingly little damage.  Hatchet Face pulled the bolt from his shoulder with no difficulty.



``Behind us!''



The camera swiftly changed direction.  A Murder Rat had landed opposite the Hatchet Face, sandwiching the group between the two villains.  The camera panned, taking in the area, and I could see the silhouettes of other villains on nearby rooftops.  More Murder Rats and Skinslips.



Hatchet Face threw the last dog aside.  It collapsed in a slurry mess of loose skin and muscle.  The dog fought its way free, shaking itself dry.  Bastard was already free.



``\emph{Fuck, fuck, fuck,}'' Imp said.  ``\emph{My power's gone.}''



``\emph{Mine too,}'' Crucible said.  ``\emph{Turned off like someone flipped a switch.}''



I closed my eyes.  I was too far away to help, couldn't think of advice to offer.



``\emph{We're not powerless,}'' Grue said.  ``\emph{We've got strong costumes.  We know how to fight.}''



Tattletale's voice came over the comms, ``\emph{He's strong enough to swing that axe through a car, tough enough you could flatten him with a steamroller and he'd get back up when you were done.}''



``\emph{We run then,}'' Grue said.  ``\emph{We deal with Murder Rat and then we scram.  Make some distance.}''



``\emph{He's not fast, but he's not a slowpoke either.  You don't have muscles like that and find yourself unable to run.}''



``\emph{Be constructive,}'' Grue said.  ``\emph{Solutions?  Options?  Any ideas?}''



``\emph{Yeah},'' Rachel said.  ``\emph{This.}''



She wheeled around, pointing.  Both of her dogs bounded towards the Murder Rat.



I couldn't see Hatchet Face with the directions the cameras were pointed, but I \emph{could} see the groups converge on Murder Rat, bull-rushing her as a mass.



Murder Rat swatted at the dogs, slashing Bastard along the ribs, but Rachel stepped in the way, blocking the follow-up attacks with the sleeves of her silk-weave jacket.



Murder Rat, about to be surrounded, leaped up to position herself on a wall, slamming her claws through a plate-glass window to grab the inside of the windowframe.  Blood ran down her wrists.



Foil took aim and fired, and Murder Rat leaped before the bolt made contact.



``\emph{She tagged the dog.  Mouse Protector's power,}'' Tattletale said.  ``\emph{Watch out.}''



A camera, Vista's, focused on the dog.



``Hatchet Face incoming!''



Clockblocker, Crucible and Toggle turned around, but Vista remained fixated on the animal.



The moment the group was distracted by the incoming titan, Murder Rat appeared.  She drove her elbow into the side of Crucible's throat, bringing one foot up to rake the side of his leg, but didn't get any further.



Vista fired her gun straight into the villain's back, then wheeled around and shot Hatchet Face in the chest.



Grue blanketed the area in darkness a moment later, the monitors going silent and dark.



I realized I'd been clenching my fists.  I loosened them, then opened and closed them a few times to ease the strain.



\emph{Escalations}, I thought.



The situation outside was worsening, but the Azazels had mobilized.  They laid down the metal poles along the tops of the wall, opening fire with their lasers.  That done, they joined the fight against the dragon-gargoyle thing that was continuing its suicidal attack against the defending capes.  Chunks of it were being blasted and torn away, but it was doing a little damage to the defending capes.



The metal poles blossomed into the branching `gray blur' nanotech barrier that would disintegrate on touch.



On the set of screens to my left, the Chicago Wards were joined by others as they ventured into what seemed to be a warzone.  Civilians were fleeing in a panic, while the heroes advanced against the press of the crowd with a steady, wary caution.



The nature of the threat became clear.  Rounding the corner, a single entity trudged forward.  It was tiny, and it bore a large white cube on its back.



To look at it, I almost thought it was an Endbringer.



It wasn't.  It was only the second-scariest member of the Nine, xeroxed.



\emph{Eight} Siberians.



One carried the cube, no doubt a container bearing the Mantons within.  The other seven followed a pattern, lazy loops that brought them back to the cube every few minutes.  They plunged through walls and into apartments and businesses, they returned with blood wicking off of their hands, feet and faces like water off a duck's back.



I opened a communications channel.



``Weaver here.  Don't fight.''



``\emph{Wasn't going to, but what the hell are we supposed to do}?'' Tecton asked.



Eight Siberians.  Even without any other members of the Nine on the sidelines, it was an impossible fight.



``You need to run.''



``\emph{Run?  The civilians-}''



``Will have to run as well,'' I said.  ``There's nothing you can do.  Accept it.  You can't slow her down, you can't deny her what she wants.''



``\emph{We have to be able to do something,}'' he said.



``There are options,'' I said, ``But it's not worth it.''



``\emph{What?  Saving civilians is-}''



``You'd die,'' I said.  ``It would be a distraction, but you'd die.  The civilians would die all the same.''



``\emph{What is it?}''



``She's still subject to gravity.  Far as I know, she can't fly.  You drop her into a hole, she'll climb out.''



``\emph{No point,}'' Grace said.



``No point,'' I agreed.  ``Unless you get lucky.''



``\emph{Lucky?}''



``Drop the one that's carrying the cube into a fissure or pit, if she falls far enough and the cube gets wedged in the crack, you'll separate her from the cube.  You'd have to destroy it before another Siberian makes contact with it, kill all of the Masters that are generating the Siberians.''



``\emph{It could work},'' Wanton said.



``Unless she moves fast enough to avoid the fissure,'' I said.  ``Which she can.  Unless she's digging her claws into the outside of the cube for a handhold, which she might be.  Unless another Siberian returns before you manage to break into that cube, which is very possible, considering that cube looks like something a Mannequin made.''



``We have Grace, and we've got Cuff.  We have Cadence and Enforce here, too.''



\emph{Enforce?  Oh.  N-Force.}



``I don't think it'll be enough,'' I said.  ``There's too many maybes.  You become a target of the Siberians the instant you try something, and you die if this doesn't work out perfectly, which it won't.''



``\emph{You want us to let civilians die.}''



I stared at the screen.  They were backing away swiftly now.  A Siberian hopped onto the top of the cube, then looked directly at the group of heroes.



A moment later, she leaped off to one side.



\emph{Flaunting their invulnerability.  Taunting}.



``Walk away,'' I said.  ``We'll send others in.  Others who can do something.''



``\emph{Who}?''



I thought of how Rachel had changed tacks, ignoring the biggest target to go after the Murder Rat.  It hadn't been much, but it had caught the villain off guard, baited the Hatchet Face into an aggressive charge rather than a slower, more strategic advance.



``Switch it up.  Go to Redfield.  You guys specialize in containing and crushing the enemy.  The Undersiders and Brockton Bay Wards can head to your location at the first opportunity.''



I didn't wait for a response.  My console was displaying an incoming message.



``Gotta go,'' I said, closing the comms channel, hanging up on Tecton.  I responded to the message.



``\emph{Defiant here}.''



``Was just about to contact the Undersiders.''



``\emph{I heard.  I'm already giving orders for them to back out.  Sent a helicopter in to pick them up, hoping it gets to take off again.''}



``Helicopter?''



``\emph{A.I. suits aren't cooperating.  I'd send one against Hatchet if they were-``}



\emph{``}Defiant?\emph{``}



\emph{``One suit just took off.  Reinforcing the Undersiders.''}



I could sense the fighting outside.  My bugs were doing precious little against Nilbog's rioting army.  The capes were whittling them down, killing them in droves, but it was time and effort taken away from containing the Nine.  Which was exactly what Jack wanted.



In the same instant Defiant had talked about the suit taking off, one of the Azazels had gone still.



Something was seriously wrong.



``\emph{What do you need, Weaver?  I have things to handle}.''



``Two years ago, I was told we couldn't go after the Nine, because we can't decode the portal without knowing the exit point.  They just used one.''



``\emph{It's in Ellisburg.}''



``It's our fastest route to Jack.  How long does it take to tap into the portal?''



``\emph{Depends on the means we use.  It doesn't matter.  The portal isn't accessible.}''



``We're \emph{losing}, Defiant.  We're winning the fights but we're \emph{losing} in the long run.  We need to act decisively.  \emph{End} this.''



``\emph{You want to use the portal entrance, knowing where it is?}''



``Yes.  We just\ldots we need capes that we can count on, on a lot of levels.  And I need your help.  Can you arrange for a sturdier ship?  The Dragonfly won't cut it.''



``\emph{Yes},'' he said.  ``That can be arranged.  I'll have to pilot it myself\emph{.}''



``If this doesn't work out, if we get overwhelmed, then that's it.  We can't afford the losses at this juncture. I get that.  But we can't afford to \emph{not} take this opportunity.''



Another pause.  Was he typing something?



``What's the status?''



``We're \emph{losing containment in Ellisburg.  Siberians are racking up casualties, and Redfield isn't doing great either.  Your Undersiders will be evacuating if they can make it another two blocks to the helicopter without getting intercepted\ldots I'm not sure what they can do against eight Siberians.}''



``More than the Chicago Wards can.  But that's not enough on it's own.  We need to call in the big guns.  We know Jack's nowhere nearby.  It's a safe time to put them into play.''



``\emph{We have people on call, but we're holding them back,}'' Defiant replied.  ``\emph{Jack will hold his strongest cards in reserve for last.  Chevalier advised that we catch him off guard.}''



``There's no point anymore.  Stop holding back.  Jack's escalating when we do.  We established a tempo, he's matching us.  Let's go all-in.  We'll get him to play every card he has on hand, and maybe in the process, we'll see him make a mistake.''



``\emph{He's not one to make mistakes.}''



``We lose nothing, and we gain time,'' I said.  ``Which big guns do we have?''



``\emph{The Thanda.  Cauldron has volunteered the services of their two elite members.  The Las Vegas Capes offered help, as did the Ambassadors.  The Alcott girl has her ability to foresee the future, but she's trying to reduce the strain she experiences so she can offer more assistance at the most critical juncture.}''



``The fight with Jack.''



``\emph{Yes.}''



``Okay.  That\ldots probably makes sense.  Listen, I'll handle what I can from here, take some of the load off your hands.  I'll see if I can't get recruits from among the capes I trust to handle their own.''



``\emph{Do.  And I would appreciate it if you would consider me one of them.  I'll be there }\emph{with the Pendragon in twenty minutes, I just need to pick up the technology for hacking the portal.''}



``Bring me some bugs when you come.''



``Yes.''



That said, he hung up.  \emph{No pleasantries}.



It was a relief.  Down to business.



\sectionbreak



Fifteen minutes to go.



I waited impatiently for the capes in question to gather.  We needed \emph{good} capes, powerful capes.  Too many were occupied elsewhere.



A whole contingent had deployed to Hyde Park.  None of my teams.  Dragon's Teeth, the New York teams, the Texas teams.



I picked Jouster's point of view.  I knew him, and it would afford me the most opportunities to see other capes and figure out their identities.



Population of three thousand five hundred, and the place was empty.  No victims, no members of the Nine.  No blood, no violence, no signs of any disruption.



But the first wave of capes had been whittled down, going silent on the radio before disappearing entirely.



Now, as the teams moved through the city, there was nothing on the video, which ruled out Nice Guy.  That left only a few options.



``\emph{Stranger protocols in effect},'' the captain of the Dragon's Teeth reported.  ``\emph{We're going full dark.  Eyes on the lightning.}``



``Eyes on the lightning,'' I responded.  For the moment, I was filling in for Dragon's absence and Defiant's preoccupation.  I knew about the Dragon's teeth, had studied their operations book.  I wasn't an armchair general, but I'd have to settle for being one here..



They were using those full-face helmets to block off all sight, to shut out all sound.  Their uniforms offered full coverage.  The only things they would rely on were video cameras on their helmets and the battle computers that were wired into their helmets.



It wasn't enough, apparently, to see anyone or anything.  Things seemed eerily quiet.



Jouster jumped as one cape cried out.  The man's back arched, first one way, then the other.



``Psychosoma,'' I reported.  ``Stranger four, master seven.  First squad, get guns trained on him, everyone else, scan the area.  Master protocols.  Confirm \emph{everything}.''



``Don't shoot without confirmation,'' someone warned, off-camera.



``How the fuck are we supposed to confirm?  Let them attack us?''



Nobody responded to that.



Still, they obeyed the instructions.  Jouster was among the ones who turned to search the surroundings.  The point of his lance was visible in the corner of the screen, as he held it ready.



Nothing.



The man screamed louder.



He \emph{twisted, }his ribs distending, his mouth yawning open.



\emph{It's an illusion}, I thought.



Kind of.  Sort of.



Not really.



It was really nice to think of it as a really convincing illusion.  That was a reassuring way of handling it.



Because the alternative was that Psychosoma was doing the sort of thing \emph{Labyrinth }did, pulling otherworldly things into our reality to replace objects and people.



When killed, they'd revert back to how they'd been before.



The man continued to twist and distort until he wasn't recognizable anymore.



The \emph{thing} whirled around, reaching back with one claw, preparing to strike at a comrade.



A cape incinerated him before he could get any further.



The illusion was dispelled.  The wrong illusion.  Purple smoke flowed out from around the corpse of the young hero.



``\emph{Nyx}!'' someone spat the word.



Jouster swiftly backed away.  Every cape in the group was wearing a gas mask, but that was not an absolute guarantee.



Two more people in the group began changing.



A mix of Psychosomas and Nyxes.  Who else?



``She's covering the area with her smoke,'' I spoke, over the channel.  ``You need to clear it.''



``On it.  \emph{Cover your eyes!}''  Jouster hollered.



Jouster raised his lance, then struck out at a light pole.  Lightning flared out, impossibly bright, and the camera briefly went on the fritz.



Somewhere in the midst of that, \emph{reality} became clear.  Bloodstains everywhere.  Corpses were draped over every surface where the investigating capes weren't likely to step – on car hoods and roofs, on light poles and in trees.



And in the midst of the crowd, there were the enemies, simply standing and observing.  Nyxes, Psychosomas and Night Hags.  The Nyx were women with pale red skin and black eyes, fog bleeding out of the vents at their arms and backs.  The Psychosomas were men, tall, bald and narrow, with pencil-thin mustaches and beards, spidery fingers and clothing that hung off them like it had been draped on.  The Night hags, by contrast, were women, dark haired, dressed in black, with skin as white as chalk.  Their dresses seemed to bleed into the surrounding landscape, so that everything within fifteen feet of them was covered in that crumpled-looking black cloth.



The Nyx clones and Psychosomas ran for cover.  The Night Hags \emph{were} the cover.  D.T. soldiers and Wards opened fire.  Hoyden struck a car with literal explosive force, and sent it flying.  Ninety percent of the offense was directed at the Night Hags.



The women practically \emph{disintegrated} as the bullets, flames and other projectiles made contact.  Their bodies shattered into thousands of black shards.



Moments later, they emerged from the landscape.  One park bench distorted and reconfigured into a new Night Hag.  That Night Hag was summarily slain, and reformed herself out of a nearby patch of grass.



Location possession, in a way, but it was shallow.  She was most effective with materials that stood above the ground's surface.



In the midst of dealing with the approaching Hags, the D.T. officers and heroes were left to handle the victims who had appeared to be transforming.  When the smoke had burned away, one had been revealed to be fine, crouching with his hands over his head, the other was still afflicted.  They shot the victim and broke the effect.



More smoke was flowing in with surprising speed and quantity, erasing the images of blood and bodies.  The Night Hags were turning translucent, nearly invisible-



And they were gone.



Jouster moved to strike the light-post again, only for black hands to grab him and pull him into darkness and illusory fog.



The image on my screen distorted, then went utterly black.



There was a sound, like a slow, wet grinding sound.  Chewing, as if from a dozen mouths at once.



I changed camera perspectives.



``--\emph{break up the fog!}''  someone shouted.  Two more of their allies were starting to change.



Someone threw a flashbang.  It didn't disrupt the smoke.



``\emph{What do we do!?}'' one of the capes shouted.  He was almost more frantic than the Dragon's Tooth soldiers around him.



The sound of a gun being cocked turned heads.



The camera turned as well.



It was Contessa, accompanied by the Number Man.  Both held guns.



She shot one of the afflicted, then walked past the other, ignoring him.  She opened fire in the fog.  One clip, each shot aimed and measured, fired with a peculiar rhythm.  One, then two in rapid succession, one, then two in rapid succession.  She reloaded with an almost casual ease, then slid the gun into its holster.



The Number Man had her back.  He fired into the darkness three times.



It took two minutes for the smoke to clear.



Two Nyx dead.  Three Psychosomas.  Four Night Hags.



The doorway was already opening for the pair to make their exit.



``Dude, who the hell are they?''



``The bogeymen,'' Hoyden said.



``Shit,'' someone said.  One of the capes.



``They're on our side?''  Another asked.



``Apparently.''



``Then why don't they go after Jack?'' a cape asked.



\emph{Because she fits in the same category as Eidolon}, I thought.  Too dangerous to allow her to make contact with the man.



I wasn't even that comfortable with them helping \emph{here}, but there weren't a lot of excellent options for thinker capes who could simply cut right through the layers of deceptions the enemy had been using.



I noted the capes who were present and still in fighting shape.  I'd hoped for Jouster.  No such luck.



I dialed Hoyden's phone, watched her pick up on the video.



``Need a hand with something,'' I said.  ``I'm going to send a ship your way.''



\sectionbreak



Ten minutes to go.



The Undersiders stood far enough away from the Siberian cube that the camera couldn't even make out the one who carried the thing.



``This,'' Imp said, ``Is your classic case of putting all your eggs in one basket.  Really.''



``\emph{He finds the Siberians boring, I imagine},'' Tattletale commented, over the channel.  ``\emph{Before, they were an enigma.  Now they're just\ldots the same thing, over and over.  Tearing people apart.''}



``Just tell me this isn't going to be the moment of idiocy that ends the world,'' I said.



``\emph{No way},'' Tattletale said.  ``\emph{I promise}.''



``You're absolutely certain?''



``\emph{Ninety\ldots three percent certain.}''



``That's not good enough.''



``\emph{Geez.  You've lost your sense of humor these past few years.  I'm kidding.  I'm sure.}''



``You've been wrong.''



``\emph{I'm right.  I swear.  Now stop fretting!}  Wait\ldots\emph{``}



The Siberians left, engaging in another brief spree, attacking civilians.



``Let's not wait too long,'' I said.  I felt a sick feeling in my gut.  Had I been right to send away the Chicago Wards?  Seven or so people were dying every one or two minutes.



``\emph{Wait\ldots}''



The last group of Siberians abandoned the cube, leaving the carrier holding it.



``\emph{Wait\ldots}''



One more returned after a very brief trip, cast a glance around, and then fled.



``\emph{Now.}''



Clockblocker fired his threads from his gauntlet.  They surrounded the cube-carrier, and he froze them.



\emph{Unstoppable force against an immovable object}.



Which won?



The Siberian made contact with the thread and flickered out of existence, and the thread went limp.  The cube fell with a crash.



Others began to return.  Vista was distorting the cube, creating gaps, weak points.



``\emph{Thanda},'' Tattletale said.



Clockblocker activated the device on his back.  A dome unfolded around him, almost like a tent, though more rigid.



Rachel had already fled with her dogs.  Even so, it was tight, everyone pressed together inside.



He froze the dome.



I regretted that I didn't get to see the follow-up attack.



The \emph{Thanda} had a cape that was sort of in the same vein as Shuffle.  A teleporter of \emph{landmasses}.



This cape didn't need to teleport things onto solid ground.  In fact, he specialized in the opposite.



A large building was teleported into the stratosphere, where it summarily fell on the cube.  I could hear the crash through the cameras the Brockton Bay Wards wore.



\emph{Siberians down}, I thought.



One more group to handle.



``Rachel's on her way to me,'' I said.  Grue was out – I didn't trust him in a face to face confrontation against the Nine, and he hadn't volunteered.  Imp was out as well.  Too risky, too much of a coin toss, whether her power would be seen through.  ``Foil?  You know what we're doing.''



``\emph{On my way.}''



``\emph{I'm coming too,}'' Parian said.



``\emph{I'll be on the comms},'' Tattletale responded.



\sectionbreak



Tecton slammed his gauntlets into the ground.  Murder Rats were knocked down from the walls.  The streets had been shattered, and the dismantled craft lay in the streets, with one dead Miasma nearby.



Another slam, combined with an activation of both piledrivers, and he created a fissure, breaking up the ground beneath the two remaining Hatchet Faces.



They made steady progress anyways.  They were too strong, their stride too long.  Tattletale had been right.  Running was difficult at best.



Cuff used her metallokinesis to heave a small disc of metal.  Effective enhanced strength, along with the ability to control the rotation of the projectile, the ability to control the flight of it after it left her hand\ldots



It slammed into a Hatchet Face's collarbone, burying into his flesh.



He broke into a run, axe held aloft.



She prepared to throw another disc, only for a Murder Rat to leap onto her from above.



The metal blades of Murder Rat's claws were swept aside as if Cuff had parried it with something physical.  Cuff settled for striking Murder Rat across the eyes with the razor edge of the discus.



Grace followed up with a crushing kick from a steel-toed boot.  A Murder Rat pounced on her, then vaulted off with enough force that Grace's head struck the ground.  Grace didn't get up.



Skinslips moved to flank, simultaneously reaching out with cloaks made of skin and shielding their real bodies with the amorphous limbs of stolen flesh.



Romp's animated constructions stumped forward, providing just as much raw mass to defend against the reaching attacks.  They picked up speed as they moved, charging like bulls, catching the Skinslips well off guard.



The fight was well in hand.  Murder Rats leaped up onto building faces so they might be able to leap down and strike a vulnerable target, but Tecton made the entire neighborhood shake.  The Murder Rats were trapped where they were, clinging to the surfaces, unable to attack.



One caught a discus with her claws, then let it fall to the ground.



No.  There was one more threat.  Tecton's helmet caught it on camera as it loomed on a nearby building.  A Mannequin.



Only it was three times the usual size.  Fat.



Cuff flung another discus.



\emph{It'll glance off}, I thought.



It penetrated.



Pressurized moisture exploded outward, crusted immediately into a small, spiky mass of ice.



\emph{Ah}.



It leaped down, and the ground shook.



Then, casually, it grabbed the most unhurt Hatchet Face with both hands and whipped its upper body a full three-hundred-and-sixty degrees around to fling him into the mass of defending heroes.



Tecton punched, his piledriver extending, but it did surprisingly little damage.



And with the Hatchet Face so close, the Chicago Wards were left powerless.  Only tinker devices worked.



The Mannequin charged.



Being a tinker, the Mannequin didn't suffer at all in the midst of Hatchet Face's power.



``\emph{Direct your attacks on the Hatchet Face, now}!'' I ordered.



A piledriver-gauntlet hit him, followed by another.  Cuff used a discus to slash at his throat, but it barely cut.



He was still alive – his power wasn't canceled out.



The Mannequin let blades extend from his wrists and elbows.   Not long, sleek, elegant blades like the original Mannequin had used, but heavy, crude ones, like axe heads.  Cuff screamed as he brought one down onto her armored shoulder.  She folded over in an awkward way as she collapsed to the ground.



He spun around, almost \emph{skipped} to one side to avoid Tecton, then directed attacks at Romp.



She took shelter behind her no-longer-animated creation, and the Mannequin-thing turned away, directing his attention at Tecton, who was trying to bash the Hatchet Face's head in.  It was a narrow window of opportunity, here.  The \emph{other}, injured Hatchet Face was approaching.  If he didn't manage it in five or so seconds, there would be \emph{two} to contend with.



A heavy bullet caught the Mannequin in the back of the head.  Ice cascaded out the back in a giant spike.



Tecton used the opportunity to slam the upper ridge of his gauntlet into the Hatchet Face's mouth and extend the piledriver full-force.



That did it.



More bullets pummeled the Mannequin.  One resulting chunk of ice partially encased Tecton, only to shatter when he pulled back.



Further shots followed, but they veered in awkward directions, sinking to hit the ground too early.



\emph{He has another power.  One that was being canceled by Hatchet Face}.



Winter's Power, I realized.



But Grace had powers now too.  She grabbed Hatchet Face's weapon and swung it, was nearly trapped in the ice that exploded out from the wound.



Romp's creation charged the ceramic man, and Tecton raised a shelf of ground around him to limit his movements.



He was being abused, battered.



Tecton's head turned, and I could see Chevalier on the camera.  Revel was beside him.



Chevalier fired his cannonblade again.  One shot to polish off the remaining Hatchet Face that was closing the distance, and another directed at the Winter-Mannequin.  The Winter-Mannequin's power took the impetus out of the second shot.



The Wards were moving slower now too.  Reacting slower.  Tecton barely resisted as the Mannequin seized him in one hand.



Didn't even get up after the Mannequin virtually \emph{punched} him into the ground.



Blades extended from his palms, the Mannequin spun like a top.



Chevalier charged, and the Mannequin changed tacks immediately, using a chain to draw himself up to a rooftop, where he clumsily climbed over the edge.



Ranged attacks didn't work, and he was deceptively dangerous in short range.



Revel launched energy-orbs, but they barely seemed to touch the Winter-Mannequin hybrid.



Then Wanton closed the distance.



Ice chipped away, and the resulting chunks flaked away at the other pieces of ice.  It was soon a localized blizzard, and the large hunks of ice that clung to the Mannequin's suit began to break away.



More ice appeared, but it, in turn, was broken by the yet-larger chunks that had been picked up.



The storm began to slow as the Winter-Mannequin concentrated his power on a smaller area.  The storm came to a standstill.



Chevalier raised his cannonblade to fire, only to stumble, dropping his weapon.



\emph{Miasma}.



``\emph{Indiscriminate attack, Chevalier!}'' I said.  ``\emph{Revel, get down!''}



Chevalier swung, very nearly striking Revel as she dropped flat to the ground.  He connected with something, and Miasma appeared in an explosion of thick green smoke.



The villain rolled, then disappeared again.



But Revel was following up, spitting orbs of energy out of her lantern.  Miasma wasn't fast enough to dodge all of them.  He, and another Miasma behind him were burned, holes the size of softballs punched through their torsos.



Cuff was helping Tecton stand, using her metallokinesis to push at his armor.  Once he was standing, they worked together to outfit Tecton with one of the specialized shots we'd prepared.



The Mannequin wasn't going to go down to fast moving projectiles or short-range attacks.



They'd take him down the same way I'd fought him ages ago.



Tecton used his piledrivers as a sort of gun, launching two cup-shaped hunks of metal with material strung between them.



The net unfolded in the air, and it draped over the Mannequin.  Spider Silk and metal wire interwoven.  It caught on the ice and the extended blades, and snagged on fingers and chains.



The Mannequin was still struggling to escape when Chevalier slowly closed the gap, bringing his sword down like a great guillotine.  He had one hand pressed to the side of his helmet.  Blood streaked down his arm.



\emph{Last group, for now.  }I watched as they checked on the injured.  Chevalier's eye had been stabbed, but not perforated, and Grace had suffered a heavy blow to the head.  Cuff's shoulder socket had been broken by the Mannequin.



I almost hated to ask.



``Tecton,'' I said.  ``We've got a game plan.  Maybe a way to get Jack.  You up for helping?''



``\emph{My team isn't in good shape.}''



``If you want to stay, keep doing this--''



``\emph{No},'' he said.  ``\emph{No.  Just\ldots maybe my team should sit the rest of this out}.''



``\emph{You've all done good work},'' Chevalier said.  ``\emph{Above and beyond the call of duty.  You don't even have to ask.}''



``\emph{I'll come on this mission, if you have a use for me},'' Tecton said.



``I do.''



``\emph{I'll come as well},'' Chevalier said.



``You're injured.''



A pause, as if waiting for me to realize what I was saying.  This was the guy that had gone up against Behemoth face to face, scarcely an hour after suffering critical injuries in an assassination attempt.



``\emph{I'll come,'' }he said, again.



``Glad to have you,'' I said.



\sectionbreak



It was suicidal.  \emph{Returning }to Nilbog's kingdom, where his creations had riled themselves up, hungry for blood.  I could only hope that their forces would be thinner towards the center, with the sustained attack on the surrounding capes.



I glanced around the back of the craft.



Chevalier.  Revel.  Hoyden.  Tecton.  Bitch.  Two dogs and Bastard.  Foil.  Parian.  Me.



Two Dragon's Teeth to round out the group, so we had people trained in the use of containment foam and other PRT munitions.  Veteran PRT soldiers outfitted with the best gear the Guild could provide.



And Defiant up at the cockpit, rounding out our group.



I felt my pulse quicken.  My hand traced over the box that Defiant had brought, with all the bugs I needed.



Nilbog's army seemed endless.  We'd only seen a fraction of it.  It flowed over, under and through the walls, in numbers that tied up the defending capes.  Our battle lines couldn't hold a position for long before \emph{something} threw them off.  Someone vital would get injured, or a creature would burrow out from beneath the ground.  Something would fly over to land in the middle of the back line, forcing a reorganization.



We weren't being \emph{overwhelmed}.  Any cape was stronger than the typical starved, desperate, reckless monster.  But this was definitely not helping.



A man's voice came over the comms.  ``\emph{Three new locations with attacks.  Coordinated strikes.  Harbingers sighted.  They are reinforced by Nilbog's creations.}``



\emph{Bonesaw got something set up already}, I thought.



Defiant was clenching his fist.



\emph{Who was the man?}



``Doesn't matter,'' Defiant said.  ``Our focus is \emph{here}.''



``Fuckin' right,'' Hoyden said.  She turned to smile at Rachel.  ``Right?''



Rachel only frowned, turning her attention to the dogs that sat between and on either side of her legs.



Hoyden punched Rachel in one arm, then grinned. ``Right?''



``Right.''



``Right!''  Hoyden grinned.



Heavy metal boots banged against the ramp as our last attendee made his way into the back of the craft.



Golem sat down opposite me, silent.  He briefly met my eyes, and I nodded.



He didn't react, casting his eyes downward.



It was nothing.  A minor thing in the grand scheme of it all.  I tried to tell myself that he was strong when it counted, whatever his doubt in the quiet moments.



The ramp closed with a bang.  Golem jumped a little at that.



It didn't do a lot for my confidence.  I glanced around at the others, wondered who else had seen it.



The Pendragon took off.



\emph{And off we go, into the lion's den.}





