





The large box sat in between the benches and seats at the back of the Pendragon, beside a heavy device with an ornate looking gyroscope on the top.  I could feel the bugs within.  I instinctively knew what they were, how they operated, and could even pinpoint exact bugs in the swarm, among dozens of their kind.



I focused on them.  It was almost meditative.  I'd taken to focusing more on the conscious uses of my power, so I'd be more aware when I was making \emph{unconscious} use of it.  There was nothing I could do about the fact that my passenger apparently had a hand in how my bugs were controlled, but I was trying to train myself to recognize it when it happened.



Rachel was focusing on her dogs in much the same way I was focused on my bugs.  Her hands ran over their bodies, fingers combing through their fur, tracing the lines in their athletic little bodies.  Bastard submitted to the touching without complaint or reaction.



I could sympathize with Rachel some, now.  We'd gathered our strike force together from among the people who I was familiar with and the people who were intact enough to fight, but my relationship to each of these people was iffy at best.  Focusing on our minions was easier.



Chevalier sat in a seat that put his back to Defiant's chair, so they faced in opposite directions.  He was talking in a low voice that didn't cut through the drone of the Pendragon's engine.  Defiant responded without taking his eyes off the controls.



Revel leaned back her head back and resting against the vibrating outer hull of the Pendragon, eyes closed, lantern in her lap.  She looked almost meditative, to the point that I didn't want to disturb her.



Tecton and Hoyden were talking in low voices.  Both were Protectorate members, now.  Tecton had passed the reins to Grace, and Hoyden was now the little fish in the big pond.  I didn't want to interject.



Parian and Foil were holding hands, sitting with their arms pressed together, heads leaning to either side so that Foil's temple sat against the top of Parian's head.  Even now, it was hard to think of them as Undersiders.  Lots of mixed feelings in the background there.  I'd turned Parian onto this path, and in the doing, I'd done the same for Foil.  For Flechette.



There was a crash, and the Pendragon shifted, almost veering into a dive.  Defiant corrected the course.  ``Passing over the wall!  One clinging to the top of the ship!''



Revel stirred.  ``Do you want me to fly out?  I can escort us in.''



``No.  The Pendragon is built to take a beating.  We're more secure with the ramp closed and everything sealed off.  Hold tight.  This is going to get worse before it gets better.''



There was another crash.  I debated sending my bugs outside, then rethought it.  No use, for much the same reason sending Revel out wasn't going to change things.



Rachel looked exceedingly uncomfortable, and the dogs were reading her body language and getting anxious as a consequence.



I winced at the sound of tearing metal, followed by a sudden shift in the ship's direction.  Something had been torn free.  Defiant corrected course again, compensating.



I wanted to say something to Rachel, to calm her or the dogs down, or simply to reach out and connect in the same way that the others in the craft were finding solidarity.  The problem was, I wasn't sure what to say.  We'd separated, had walked different paths, and I'd betrayed her on a level.  I'd led her to believe she had a friend in me, and then I'd walked away.



She met my eyes, scratched Bastard at the top of his head, then asked, ``What?''



``You're okay?''



``Yup,'' she said.  She didn't \emph{look} okay.  She stroked two different dogs, but I almost felt like the gesture was more for her sake than for the dogs.



``Not right now.  Just\ldots in general?  Are you okay in general?  Living on the other world?''



``Yup,'' she said.



I sighed, turning my attention back to the box.



``I'm hoping my dogs are okay,'' she said, staring down at the metal floor.  ``Been a while since I've been away from them like this.''



``You have people, right?  People you\ldots'' I let the sentence hang as I tried to recall whether \emph{trained} was something appropriate for people and not dogs.  ``People you trained, to look after your dogs.''



``Yeah,'' Rachel said.



``Setting down!'' Defiant called out.



There was another tearing sound, like nails on a blackboard scaled up to a volume that made it resonate in my bones.  Maybe the worst sound I'd ever heard.



Just that thought brought back recollections.  The dull, faint sound of an old doctor's body hitting the ground, after Mannequin cut her throat.  My dad's voice, crying my name, sounding very distant despite the fact that he was right next to me, in the moments before I killed Alexandria and Director Tagg.  The non-sounds Brian had made as he'd opened his mouth, noises so quiet they weren't even whispers, as he hung in the refrigerator, post-Bonesaw, pre-second trigger event.



No, there were worse sounds than the screech of metal tearing.  Sounds I'd barely registered at the time, but nonetheless sounds that haunted me.



``Tattletale sent us some old guy to teach us how to butcher the bison,'' Rachel said.  ``None of the others are any good at it, and it's harder without the dogs there to help haul it off the ground by its back legs.''



The Pendragon set down.



``Taking off will be harder than landing was,'' Defiant said.  He didn't flinch as a creature pounced on the glass of the ship's windshield.



A heartbeat later, \emph{something} hit the outside of the craft.  Something big.  The thing on top that was tearing at the metal struck again, no doubt peeling away at an armor panel.



``--And I'm thinking they're probably getting hungry.  Fucking up good meat, not carving out the fatty bits.  Or they aren't getting all the blood out.  You have to cut \emph{deep }to bleed\emph{ }the motherfuckers.''



Distracted by the landing, some of the junior heroes were paying attention to Rachel now.



``What the \emph{hell} is she talking about?'' Hoyden asked.



``Don't worry about it,'' I said.  Then I glanced at Rachel.  ``Either of you.  Rachel, they're going to manage fine.''



``They're going to manage,'' she said.



Defiant was already out of his seat.  He had approached the device he'd placed next to my box and managed to get it going just as Rachel finished speaking.



Every monitor in the Pendragon's cabin flared to life.  Countdown timers appeared, white numbers on a black background, with fainter, smaller timers above and below.  I knew they would be the minimum and maximum times.  The one in the middle was only an estimate.



The craft was struck again, and a dent in the outer walls nearly knocked Tecton from his seat.  Everyone reached for something to hold on to, as the Pendragon nearly tipped over onto its side.  The dogs barked at the disturbance.



``There are forcefield generators,'' Defiant said.  ``But they take time to recharge.  We'll hold out for as long as we can before using it, waiting until they are more numerous, and our options are limited.''



``Four minutes,'' Tecton observed, looking at the monitors.



``We- \emph{I} think so\emph{,}'' Defiant said.  ``Plus or minus one minute and thirty seconds.  The forcefield generator is housed in the underside of the craft, to provide stronger defense from below.  It'll last after the walls come down.''



``Defensive positions,'' Chevalier said.



``Protecting the decoder is a priority,'' Defiant said.



We stood from our seats, backing towards the center of the craft, the decoder and my box of bugs at our center.  I reached back and opened the box, letting the bugs flow out.



Without my even asking, Defiant opened the ramp at the back a fraction.  Like a flower blossoming, slowly at first, then with increasing speed, I could feel my awareness expanding.  I could feel the outside of the ship, the creatures that were gathering in ever-increasing numbers.  Every shape and size imaginable.



Three were making good headway against us.  I could identify the same creature, I was pretty sure, that had been pummeling the wall at the outer perimeter of Ellisburg.  It was a quadruped, and it moved with a surprising slowness as it paced away from us.  Strands of fur longer than I was tall hung off it, and its head was one armored plate with eyeholes, the edges flaring out and away from its head at the sides and back, allowing its long, pointed ears to freely move behind the plate.  It lowered its head in the direction of the craft and tested the ground with one scuff of a spike-studded hoof against the pavement.



I set bugs to attacking its eyes, driving them into ear canals in hopes of distorting its sense of direction.  It aborted the charge to shake its head violently.



``Possible incoming right in front of you, Tecton.  Any second now.''



``Right,'' he said.  He held his ground.



``Might be worth moving,'' I said.



He looked back at me.  ``Aren't we supposed to defend the decoder?''



``Switch,'' Chevalier said, with no elaboration.  Tecton hurried to take up Chevalier's position towards the nose of the craft, while Chevalier lowered his cannonblade in the direction of the bulge on the wall.



There were two more creatures that were gouging the hull.  One used oversized claws to pry at metal plates.  Another was drooling acid onto the roof.



I could sense the round-headed bald girl from earlier as well, one creature that moved with a startling speed as it scratched at the outer edges of the craft, one way, then the other, so the gouges in the metal formed hatch marks.  Burrowing, almost.  Burrowing very slowly.



Something howled, and it was \emph{loud}.



The creations were piling around the craft, with a number gathering on the window over the cockpit.  Tecton tensed.



``The window is stronger than the metal,'' Defiant said.  ``Don't panic.''



``It isn't as flexible,'' Tecton said.  ``One good hit like the one that dented the wall there and it won't hold up.''



``It's designed to take rocket launcher hits head on,'' Defiant said.



``That doesn't mean it's designed to take them from an \emph{angle},'' Tecton retorted.  ``My power gives me a sense of structural integrity.  I'm saying I'm worried.''



``Fine,'' Defiant said.  He watched the ramp, not moving an inch.  ``Be worried.''



The charger was incapacitated, its eyes devoured, eardrums perforated, with bugs crawling through the middle ear fluids that were pouring down its ear canals..  I diverted bugs to the thing that was clawing the armor plates off of the outer edges.



An instant later, the charger lunged forward.



No sense of direction, no ability to see, not even any balance, beyond what its four legs offered.



But it was big, and its target was big as well.



``Heads up!'' I shouted.



It slammed into the side of the Pendragon, closer to the back than the location of the first hit.  The metal tore where two sections joined together, and a monitor fell to the floor, shattering.



Creatures began crawling through the gap.  Defiant moved his spear to the opening, then activated the gray blur.  He held it there, allowing them to die and be wounded on contact.



Golem used his power, raising a hand of metal to cover the opening.



Defiant lowered his spear and canceled out the blur.



The disintegration effect might have been worth keeping on hand, but I could understand if he was concerned about another impact knocking someone into the spearhead.



Creatures had hopped onto the charger's back, and were helping guide it, babbling and screeching, tugging on its fur.  It followed their directions, retreating.



I directed my bugs to attack, stinging and biting each of them on the same general side.  They reacted, tugging and pulling away, and the charger changed direction.  Only his flank glanced the back of the craft, and he trampled through a crowd of the little bastards who'd congregated on and around the ramp.



The round-headed girl sat there, half-crushed, and then began to swell.



``Heads up!  Your left, Defiant!'' I shouted.



She detonated, and gunk spattered the ramp.  I felt bugs die on contact.



The ramp began to melt like candle wax.



I moved bugs to the fray while Hoyden and Defiant advanced on the ramp.



The creatures came in as a singular mass.  Dozens at once, practically crawling over one another.  A spine glanced off of Defiant's armor and came within inches of striking the decoder.  Foil swatted it out of the air.



Parian's first doll joined Rachel's dogs in reinforcing the space behind Hoyden and Defiant.  Hoyden kicked and punched at the creatures, and small explosions tore through their ranks.  One punch, two or three creatures dead.  One landed on her, claws extended, and then promptly flew away as another detonation of flame and smoke flared from the point of contact.  She was barely scratched.



If those claws were poisonous, though\ldots



Still, she made for a competent front line, beside Defiant with his disintegrating spear.  Every movement of the spear was as precise as Hoyden's explosions were erratic.  The blur effect cut through the enemy like butter, and in the rare occasions where the target did slip away or dodge the attack, Defiant followed up with jolts of electricity and darts.



The charger steered around and began to pick up speed.



``Chev, incoming!''



I tried to distract the charger again, targeting the riders, but it didn't work.  This time, they pulled in different directions, or simply dropped off.  It continued on course.



It struck only two or three feet to the left of the first point of damage, and opened up the side.  The thing with claws on the roof, squinting against the steady damage my bugs were doing, hopped over and began to pry the gap open wider.



I moved a swarm over the gap, trying to hide the entryway, but it did little good.  Both Parian and Rachel shifted position to defend the opening.  Golem began trying to patch it up.



``Careful!'' Defiant warned, glancing over one shoulder.  ``Too much extra weight and we won't be able to take off!  Containment foam instead!''



The perils of physics-defying powers.  Golem and Rachel both broke the laws of conservation of mass, and now we risked paying for that.  The Dragon's Teeth stepped forward to take over.



I could see the charger turning around.  One creature was on its back, a heavily armored thing that had hard, multifaceted eyes like an insect.  My own bugs couldn't damage the orbs.  It cheered in a high voice, urging the charger on, with some English words peppered in the midst of its gibbering.



One more minute to go.  If we were lucky, it could open any second.  If we were unlucky, it would take two and a half minutes.



Two crawled in through the crack in the side, clinging to the ceiling as they made their way in through the cloud of bugs.  I pointed, and Foil slashed at them with her rapier.  Tecton squashed another with his piledriver.



Over where another of the creatures had been trying to burrow into the side, a creature pushed it aside and \emph{spat}.  The effect was the same as the exploding bubble-head girl from earlier, if less dramatic.  Looking at the exterior wall, I could see the hatch-marks appearing in the side as though they'd been drawn in marker, pale against the dark metal.  They spread, the effect broadening, until the hatch marks were drawn out in white and the surrounding area was paler.



Something punched through, then reached in blindly to scratch and claw.  Golem's reaching hand broke the claw.



More spots were appearing, though.  Dents, gouges, acid\ldots  I attacked the creatures that were doing the most damage, as far as I could identify them, but there were more waiting to take their places.



``Nilbog's creatures!''  I spoke, raising my voice.  I spoke through my bugs outside.  ``We mean no harm!  We will bring you back your king!''



Nothing but cries of rage and hate in response.  No use.



Thirty seconds, now.



The holes in the exterior opened enough for the creatures to start pushing through.  The acid burned them where they made contact, but that same contact opened the holes wide enough for others to follow.



The charger lunged, charging again.  There was really only one rider it was listening to, but that pilot was a tough one to hurt.



The thing screamed one word in English, twice in quick succession, its voice high,



``Jump!  Jump!''



The charger leaped.  The result wasn't graceful, nor was it particularly on target.  What it \emph{did} do was allow the charger to get one foot up on the side of the Pendragon, its upper body partially on the roof.  It kicked and struggled in its attempts to move forward, and found one leg caught in the tear it had made on its last charge.



It placed the foot on top of the hands Golem had raised to block the gap, and sheer weight tore them down.  It slumped, falling, and then brought the end of its nose inside the ship, dragging it against the tear in fits of thrusting, struggling to free both it and its leg, succeeding only in doing more damage.  Reinforced shafts and beams held against the damage, but could see how each wiggle was bending the thick bars.



``I thought you said this thing was tough!''  Foil shouted.



``It \emph{is},'' Defiant said.



``Forcefield might be a good idea!''  I called out.



Defiant didn't respond.  Hoyden had made her way down the ramp and was dishing out the hurt close-range.  She was keeping the melee threats on their heels with a constant, aggressive offense, while her secondary powers rendered her resistant to the damage that came from a distance.  Defiant was left to defend the opening himself.



I drew my knife and my handgun and advanced until I was just behind and to the left of Defiant\emph{.  }He shifted position a fraction, allowing for the extra assistance.



\emph{Who knew we'd get to this point, Armsmaster}?  I thought.



Fighting side by side.  I used my knife to impale one creature in the neck, then kicked it back down the half-ruined ramp.



Two of the countdown clocks had hit zero.  The one clock remained.  The high end of Defiant's estimation on the decoder's progress.



``One minute,'' I said.



``Maybe,'' Defiant said.



``\emph{Maybe}?''



``We took the time this past year to find Dodge's old exit points, talking to ex-customers of the--'' he stopped, grunting as he swept the spear at one persistent spine-spitter, ``--Toybox group.  Used it to get readings, test the decoder.  But \emph{this} portal has different metrics, updated technology.  More recent tech.''



``It's not a \emph{guarantee}?''  Hoyden shouted the words, as explosions continued to rip out around her, tearing through the assembled creatures.  They were keeping a healthy distance, now, which meant her very presence was keeping a whole area clear of the blighters.



\emph{Nothing's a guarantee}, I thought.



``I never guarantee anything,'' Defiant grunted, echoing my thoughts.  ``Except for a select few promises I make to people I love and people I hate.''



Rachel's dogs were tearing into the goblins as they made their way through the gap beneath the charger that had wedged into the gap, each dog biting their mouths down once or twice in quick succession before flinging the things away just so they could have their mouths free to bite \emph{others}.  Their paws swept out to club and claw at the creatures.  Tecton and Foil guarded the space between dogs, striking out to catch the ones which slipped between the dog's legs.



I plunged my knife down to stab one of the softer looking targets, then danced back to avoid the spatter of acid that flowed from the wound.



``I'm getting buried!'' Hoyden shrieked.  She'd been targeted by some critters that were dissolving into a slurry as they burned, with tendrils extending out to draw in the wounded and dead.



\emph{They're reincarnating, feeding on themselves to make more}.



``Stop using your power!'' Defiant ordered.



``I \emph{can't}!  They'll kill me!''



I glanced over my shoulder at the clock, then whipped my head back around as a creature pounced, trying to wrap itself around my head.  I shot it, feeling a flare of relief that I hadn't just been killed, mingled with a regret over the loss of the bullet.



``How is it not done yet!?'' I shouted.  ``Zero on the clock!''



Defiant didn't respond.



``Defiant!  Do we take off!?''



The charger, still caught in the gap, found the leverage to strain against one of the reinforcing girders that maintained the craft's structure.  It began to slide down, and Golem raised a stainless steel hand to keep it from stomping on the decoder.



The hand wouldn't be strong enough.  If that thing shifted its weight any more-



``Defiant!'' Tecton shouted.  ``What are our priorities!?  Can we take off?''



``No,'' Defiant responded.  ``We stay.  Wait, cross our fingers.''



I glanced back to see Golem and Tecton exchanging a glance.  The creature struggled again, sudden, and the beams shifted further.  One more struggle like that, and the little hand wouldn't hold it up.



A big hand, though, might cement our fate, take away our maneuverability.



``Saint,'' Defiant said.



I glanced back at him.



``Don't fuck us on this.  We need those Azazels.  We need an escape route.''



\emph{Saint}?



The fact that Dragon was debilitated was another trick, an extremely ill-advised play against the heroes, capitalizing on our distraction with something greater.



``I'm going to fucking kill Saint,'' I said.



``If we survive this fucking-,'' Tecton said.  He grunted and fell on his armored rear end as a dog jerked to one side, accidentally body-checking him.



``Not a suicide mission,'' Defiant said, carrying out only one half of a conversation we weren't entirely privy to.  ``Back us up, \emph{now}.''



A pause.



Defiant spoke, and his tone of voice had changed.  He wasn't talking to Saint.



``Toronto, Ontario.  Canada.  Yonge Street.  Just behind a place called Greenway.  I've commissioned a thinker-investigator calling himself Gleer to track them down.  If only some of us make it, do me a favor, and remember that Saint is the one who fucked with one of our biggest truces yet.  Saint took down Dragon, and he just left us to die.  The Azazels are apparently better deployed elsewhere.''



The charger bucked, and Golem created a large hand, not to catch the descending foot, but to divert its direction.  It crushed my empty bug box.



This much weight on the craft, the loss of so many external components\ldots we wouldn't be able to fly.



The roof came partially off.  More streamed in through the resulting gap, dropping down into the middle of the cabin.



Revel unleashed her lantern.  Spheres of light and flame flew out in every direction, burning through the ranks of the smaller creatures, zig-zagging to maximize contact between them.  The charger died, going limp.



A moment's reprieve.



Defiant used a grappling hook from his glove to try to catch Hoyden, only for it to fly off in another blast of flame.



He tried again, but this time, he whipped the chain, so the length of it wound around her, then yanked her inside.  He signaled, and the forcefield went on.  In seconds, we cleared the few that had survived from the Pendragon's cabin.



Creatures died as they made contact with the field.



Defiant dropped his spear, turning to the device that Dodge had set up.  Data appeared on the monitor.



``Give me a connect to Alcott,'' he said.



Tattletale's voice sounded through my earbud.  ``\emph{You sure?  You know}--''



``Time is of the essence.  Now.''



``\emph{Righty-o}.''



The rest of us exchanged glances.  Rachel was tending to her dogs, Parian was binding wounds with spare cloth and creating more constructs, and Golem was patching up the damage.  Not \emph{fixing} anything, but barricading.



``\emph{She's on the line.}''



``Top half of the list, success?''



``\emph{Zero,}'' Tattletale said.



``Last quarter?''



``\emph{Yes}.''



Defiant typed on the keyboard.  ``That's it.  Narrowing down possibilities.  Thank you.''



We waited, looking through the spaces where the barricades hadn't yet gone up, at the creatures that waited.  Hoyden submitted to some bandaging on Parian's part.



I watched the forcefield flicker.  It seemed to coincide with what Defiant was typing on the keyboard.  A strike of the enter key, and it flickered and went out.



``I'm taking it down early,'' Defiant said.  ``We need the power.''



Barely a minute.



The creatures approached hesitantly, then broke into a run.  I could see the dogs tense.



``Back up,'' Defiant said.  ``Now.  Huddle!''



We did, swiftly retreating until we were clustered around the center of the cabin, shoulder to shoulder, our backs to the device. My bugs filled the gaps.  The creatures, in turn, gibbered, squealed, screeched and roared.  They howled and stomped and drummed fists on chests.



Impacts made Golem's hands bend, and I could hear a dozen points where they were grabbing at the plates of metal and straining to bend and peel them.  That horrible sound, in innumerable places around the craft.



And then silence.  Darkness.  Air rushed around us, equalizing throughout a vast, empty space.



\emph{Out of the frying pan and into the fire}, I thought.



We broke the huddle, our headlights and flashlights going on.  Rachel's dogs could be seen in the darkness, their eyes glowing red and orange in the reflected light.



``It seems we have company,'' Jack said.



I could see the others startle.



``No, I'm not standing next to you.  Borrowing Screamer's power to broadcast, to have a little chat.''



No.  Couldn't afford to listen to him.  If any of us were problematic, or if it was someone listening in, anything he said could be the catalyst for the end of the world.



Problem was, Screamer was a \emph{bitch} to shut down.  Ear plugs wouldn't be any guarantee.  If she was forced to, she would use the vibrations of people's\emph{ bone}\emph{s} to transmit words.



Jack continued, ``I confess, I do like this part.  The \emph{chatting}.  It's safe to keep my distance, but it's boring, really.  You challenge somebody, pit mind against mind, but how much do you truly get to know them?''



``Move,'' I said.  ``Fan out, find Screamer as soon as possible.''



My bugs flowed out in advance of the group.



``This, the conversation, it's what turns a mindless killing spree into something more, an \emph{art}.  Bonesaw is fond of telling me that true art speaks for itself, but really, there needs to be a relationship between the artist and audience, if only because there's a lot of idiots out there.  Some people need it spelled out for them.  Hi Theodore.''



Golem clenched his fists.



The area was vast and empty.  Every surface was granite, rough but not so much so that it would be painful to walk on with bare feet.  The wiring was crude, small floodlamps strung out in strings, like oversized, colorless, exceptionally boring Christmas lights.  Wires had been stapled against the walls, fixing them in straight lines, but the excess draped loose at the bases of those same walls.



The lights were bright, but they only covered two-thirds of the area.  The spaces between those same lights were dark to the point of being almost pitch black, the afterimages in my vision making it look like things were moving in the shadow.



``Gray Boy is retrieving your sister this very moment, Theodore.''



Golem stopped in his tracks.



``Yes,'' Jack said.  No elaboration.  Answering a question that hadn't been asked.



``Can't communicate with our people while we're here,'' Defiant said.



``Keep moving,'' Chevalier gave the order.



Jack spoke, his voice smooth.  Or Screamer spoke, mimicking what he was saying, quite possibly in the exact tone and cadence.  ``We got video.  I thought about having it be silent, in black and white, but Gray Boy wanted color.''



My scout-bugs found no signs of life.  Only bizarre constructions.  Crystal pillars with more wires stringing to them?  Where was Jack?  We passed through a room with what looked like a dentist's chair.  Tools and pieces of the mechanical scalpel-spiders littered the room.



Bonesaw's operating room.



``I like to think this is a win-win situation for me,'' Jack said.  ``Wait until you \emph{hear}.  We'll get the video up in a moment.  Play it on the speakers, maybe, or show it on the computers, if you can find one soon.  Does this break you, or does it give you that burning fury that drives you to go the extra mile and try to kill me?''



We entered the main area, and I stared.



``Oh god,'' Foil said.



There was a crunching sound as Chevalier let his sword drop, the metal biting into the floor.



The crystalline pillars were \emph{vats}.  Cloning vats.  Each marked with a name of one of the Nine.



They were full.  Babies floated within each.



``Cherish says you found the clones.  Yes.  We're doing another batch.  Didn't take much time to prepare, and it was bound to be either a nice follow-up or a good surprise for you if you \emph{happened }to catch up to us here.  You \emph{know} I'm close.  Do you take the time to eliminate each of these things, or do you come after me and leave them behind?''



``We can have someone stay behind, clean up,'' Chevalier said.



``I wouldn't say that, Chevalier,'' Jack responded, his voice carrying through the vast chamber with two or three hundred vats spaced evenly throughout.  ``See, we mixed things up a little.  There's a specialized cleanup area that can kill the Crawler clones.  We gave them their powers right off the bat.  Mixed them in with the others.  You'll have to be fairly \emph{discerning}, and devote manpower to the task.''



I thought about using my power, but there weren't any bugs native to this area.  I was limited to the ones that I'd brought with me.  Not enough to cart two or three hundred children off to some special device.



``A distraction,'' Defiant said.  ``There's another option.  A bomb.  If we track down the device Dodge used to create and maintain this dimension, we can collapse it.''



``How fast?'' Chevalier asked.



``Fast,'' Defiant answered.



``Poor sportsmanship,''  Jack rebuked them.  ``Let's try a different distraction then.''



A computer monitor on the desk flickered to life.



``I'm excited,'' Jack said.  ``Gray Boy is working on getting the video up.  Funny thing.  The \emph{real} Gray Boy wouldn't be able to do this, but we gave this one the memories of a real child.  Came with the necessary skills.  I'm almost disappointed.  People are so much more interesting when they're flawed, aren't they?  Oh, here we go.  I haven't even seen this.  Let's see\ldots''



The video started playing.  The camera wiggled and wobbled as Gray Boy ascended a staircase.



He came face to face with PRT officers.



``Best not to watch,'' Revel said, her voice gentle.  ``It's not worth it.''



Golem didn't take his eyes off the screen.  Revel approached him, putting one hand on his shoulder.



Others turned to keep scouting the area.



I joined them.  This place was \emph{massive}, but my power had range.  I needed to find Jack, and that was a bigger priority than seeing the scene as it played out.  Rachel walked between the rows and columns of glass vats with me.  Her dogs trailed behind, their spikes and spurs occasionally tapping or dragging against the glass of the vats.



``\emph{There we go},'' Gray Boy said, his voice high, as he spoke in the video.  I could barely make it out with my own ears, but I had my bugs to help.  It didn't hurt that the ones who'd remained behind were utterly silent as they watched.



I'd already seen, in a sense.  I'd figured out what was behind the tarp back in Killington.  Gray Boy's victim.  The only one, as far as I was aware, who was still alive.



But Gray Boy didn't kill.



``\emph{Let's adjust\ldots there,}'' Gray Boy said.



``\emph{Please\ldots don't\ldots please\ldots let\ldots}''



The voice was halting, cut short at steady, regular intervals.



``\emph{Me\ldots go\ldots please\ldots oh\ldots god\ldots}''



``\emph{Shhhh},'' Gray Boy's voice was a hush, but it carried through the speakers that were planted throughout the area.



``\emph{I\ldots don't\ldots}''



``\emph{I said be quiet},'' Gray Boy said.  ``\emph{I'll do you a favor, even.  I can make this painless.}\emph{I just need you to talk to me.  Tell me a story.}''



``\emph{A\ldots story\ldots?}''



``\emph{I'm sure you can come up with something good.  Let's start with your partner.}''



There was a scream.  I tensed.



The scream didn't stop.  It continued, a steady, constant loop, the beginning the same, the ending varying.



``\emph{What\ldots story}?''



The scream changed, intensifying.  It continued looping, just a little louder, a little less usual.



``\emph{Don't be a baby},'' Gray Boy said.  ``\emph{That's only a pocket knife I cut you with.}''



``\emph{Trucks\ldots vampir\ldots dragons\ldots what\ldots do\ldots you\ldots want\ldots}''



``\emph{Think about it,}'' Gray Boy said.  ``\emph{When I come back, I want to hear it.  If it isn't a good one, I'm going to light a match.  They say a burn hurts more than any other kind of pain, inch for inch.  Look, see!  I've got a whole matchbox here.  A whole matchbox just for you two, and all the time in the world.}''



The man's oddly rhythmic screaming continued, dropping in volume.  It was barely audible as a door shut.



I forced myself to keep walking, exploring with my bugs.  Tunnels, side-rooms, many occupied with old devices, things belonging to the Toybox residents that had apparently claimed spaces in here for themselves.



``Can your dogs pick up a scent?'' I asked.



Rachel shook her head.  ``Wrong breeds.  They're not trained in tracking people.''



I swore under my breath.



``Kayden.''



Golem's voice, from far away.



Gray Boy had found Theo's family.



``\emph{Move your hand},'' Gray Boy said.  ``\emph{You know it won't work.  I'm too hard to kill.}''



A pause.



``\emph{I'm going to give you a choice.  You can put the little girl down and let me have her, and then I'll use my power on you only, or I can use my power on you both}.''



There was no reply.



``\emph{Don't be silly},'' Gray Boy warned.  His tone was flat, almost without affect.  ``\emph{Give me the girl.  I promise I won't do anything to her.  Can't say the same for any of the others, but you and I both know that nothing they can do even compares to what happens when I use my power.}''



A sound.  A whimper.



``\emph{I'll even let you choose.  What kind of hell do you want to go to?  I can use fire, or knives, or I can hit you with something heavy.  I like that little statue over there.  There's cold, probably.}''



A sound, a bang, a crash, echoed over the speakers.



I continued pacing down the row of vats.  I reached the end, then traversed an open, empty space before reaching the start of a complicated, almost labyrinthine tunnel network.  My bugs struggled to trace the contours of the space and find their way to the next area.



When they did, they found it was an even bigger space than the one Rachel and I were in.  A giant robot stood in the center, half-complete.



A toddler started shrieking, her wail audible over a hundred speakers throughout the complex, each just a fraction out of sync with the others, given the speed of the signal traveling as compared to the speed of the ensuing sounds.



``\emph{Not bright},'' Gray Boy said.  ``\emph{And the baby's crying.  No wonder, with you trying to throw her out the window.}''



There was only silence in response.



``\emph{I thought you'd use your laser instead.  Do you think your baby can fly?  Here.  I'll make the loop longer so you can talk.}''



``\emph{I\ldots had\ldots to\ldots try\ldots}''



``\emph{Maybe.  But now I have to punish you.  I could hurt you, like I do with most people.  Hurt you while you're looping through the same action, so you feel that pain over and over and over and over again.  The only thing that doesn't change is your brain.  That keeps going.  The pain is always fresh, it never gets easier to deal with, but I'm told there's a certain point where you crack, and you go around the bend.  Takes a few days for most.  Then you get to a point where you work through your issues.  You don't want to, but you do, because the only thing you have to occupy yourself with is the pain and your own thoughts\ldots so you get mostly better, and then you crack up again, and you get better, and that becomes a loop of its own\ldots}''



``\emph{Fuck\ldots you\ldots}''



``\emph{Until well after the sun goes out, they think},'' Gray Boy said.  ``\emph{Speed of thought, can't turn it off unless I'm using it on myself, and I don't think anyone's immune.}''



``\emph{Bastar\ldots d\ldots}''



``\emph{But I do that to everyone I use my power on.  Like a snap of my fingers, just like that, anyone around me is caught in a loop.  What kind of special punishment could I give you, murdermommy?}''



There was no reply.  The child continued to cry.



``\emph{Who's this one?  The woman?'' } Gray Boy asked.  ``\emph{No answer?  How about\ldots now}.''



There was a pause.



``\emph{Most scream when you stab them.}\emph{Oh well.  Maybe this one?}''



I changed direction, walking along the wall to get a sense of the greater complex.  There was no way to check the area at the foot of the giant robot without navigating the labyrinth.  My range wasn't that long.



``\emph{Nope.  And\ldots this one!''}



\emph{A scream.}



``\emph{There we go.}''



``\emph{Crusader\ldots}''



``\emph{I've decided, murdermommy.  I won't do anything to you for now.  I'll let you wonder what the others did to your little girl.  Then, maybe, if she's still alive, I'll bring her back to you and I'll use my power on her while you watch.  Maybe a week from now, maybe a month, maybe years.  Decades, even.  A hundred years?  They have cryogenics and brain scans and cloning vats and more!  We could show up a thousand years from now, just to say hi to you.}''



``\emph{No\ldots}''



``\emph{You lose track of time, like that.  Standing there.  But maybe if you keep yourself sane, you'll be able to offer advice so it won't be}\emph{so unbearable, so you can converse and tell stories and keep each other happy}.\emph{  Maybe, if you keep it together enough, you can convince me to let her go.  I'll give you a\ldots one in twenty chance.}''



``\emph{No\ldots}''



``\emph{Tell her to listen to me.  To obey me.  You know what happens if she doesn't.  Convince her.}''



``\emph{Aster\ldots do\ldots what\ldots he\ldots says\ldots}''



``\emph{Good.  You hear that, Aster?  Good.}''



``\emph{Come\ldots back\ldots}''



Her voice was quieter, almost drowned out by Aster's wailing.



A door shut, the speakers echoing the sound all throughout the complex.



The rhythmic screaming of the PRT officer grew louder.



``\emph{Sit},'' Gray Boy's high voice sounded.  ``\emph{Don't run, little girl.  Listen to me like mommy said.}''



The man's screaming grew louder still.



``\emph{So whiny.  I just cut up his face.  So?  Tell me a story?}''



Silence.



``\emph{Okay.}''



A sound of a match being struck.



``\emph{We\ldots were\ldots briefed\ldots on\ldots Jack\ldots  we\ldots don't\ldots know\ldots how\ldots he\ldots ends\ldots the\ldots world\ldots we're\ldots suppose\ldots to\ldots implemen\ldots quarant\ldots ine\ldots''}



I stopped in my tracks.



``\emph{He\ldots talks\ldots to\ldots someone\ldots and\ldots catalyz\ldots es\ldots someth\ldots ing\ldots}''



The PRT officer had been asked to weigh an eternity of torment against the lives of billions, and she'd chosen the selfish option.



``\emph{Every\ldots major\ldots group\ldots helping\ldots teams\ldots defeat\ldots Jack\ldots  Cauldron\ldots Thanda\ldots PRT\ldots Protector\ldots ate\ldots Wards\ldots Brockton B\ldots ay villains\ldots Moord Nag\ldots Irregulars\ldots Faultline\ldots Triumvirate\ldots''}



We'd just lost our last major advantage in determining how this could play out.  Jack was getting everything.  He was a wiki-walk away from getting details on everyone who was arrayed against his new Slaughterhouse Nine.



I could sense the others as they moved through the complex.  I beckoned Rachel and her dogs, then mounted up.



I kicked the dog into motion.



``\emph{Others\ldots I\ldots can't\ldots recall\ldots  they\ldots are\ldots keeping\ldots powerful\ldots people\ldots away\ldots from\ldots Jack\ldots to\ldots avoid\ldots catalyz\ldots ing\ldots they\ldots are\ldots employing\ldots strike\ldots teams\ldots to\ldots take\ldots down\ldots smaller\ldots groups\ldots''}



``\emph{And you're here because?}''



``\emph{Because\ldots Aster\ldots supposed\ldots trigger\ldots young\ldots usually\ldots one\ldots child\ldots in\ldots family\ldots know\ldots Jack\ldots coming\ldots probably\ldots in\ldots person\ldots chance\ldots she\ldots is\ldots catalyst\ldots}''



``\emph{There's a lot of people who could be the catalyst,}'' Gray Boy said.  ``\emph{You'll drive yourself crazy trying to cover all of the bases.''}



``\emph{Low\ldots chance\ldots but\ldots still\ldots chance\ldots thought\ldots we\ldots could\ldots protect\ldots with\ldots Night\ldots Fog\ldots Purity\ldots Crusader\ldots''}



``\emph{Well},'' Gray Boy said.  ``\emph{That was boring.  I wanted a story with neat monsters}.''



I gave serious consideration to switching the earbuds to a setting that would make them serve as earplugs.  I made myself keep listening as the screaming started, keeping my ears peeled for clues.



My swarm-sense, at the same time, was searching more of the area.  I brought bugs to me, then sent them off into new corridors as I reached them.



Too few bugs in this entire place.  No moisture to feed them, no food sources.  Only a scant few that had no doubt been brought in accidentally.



``\emph{I} thought the story was interesting,'' Jack said, his voice sounding as though he were speaking in my ear.  ``See, I had a plan in mind, but now I'm rethinking it.  If \emph{I'm} supposed to be a catalyst, then it can't be any of the others.  Bonesaw would get the credit for any plagues or clone armies we deployed, even if I gave the order.''



I grit my teeth.



``But if the effect is \emph{broad}, well, giving the order could be a part of it.  Our Harbinger has been giving us some very good advice.  Talking about the critical places to strike.  What happens if we attack certain targets?  The world teeters on the brink of falling to the Endbringers.  Divide my remaining soldiers and attack key points in the infrastructure, and maybe that's game over for humanity.''



``\emph{Here}.''  A voice over the comms.



Or Screamer fucking with our heads?



``Verify.'' I spoke over the comms.



Nobody called back to verify.  A sign I was on the right track?  I kicked the dog to drive him to move faster.



``Or if Gray Boy uses his power on Scion, perhaps?  We could assassinate some key figures.  Win-win, because we either deliver a critical blow or we might run into the right person to bring about the end of the world.  So many possibilities, really.''



I could sense them.  Easily two hundred of the Nine, accompanied by a mess of Nilbog's creations, hooked up to Bonesaw's control frames.  Nilbog hung on the wall above the group, limbs splayed, tubes feeding into him as blobs dropped down and were captured by a small army of mechanical soldiers.



I closed my eyes for a moment.  A trick?



No.



Two years of emotions caught up with me in a single instant.  I felt fear grip me, anxiety seizing my entire body, adrenaline flooding through my body.



Yet, when I spoke, my voice was calm.  ``Weaver here.  I'm using my first priority passphrase.  Danny and the Rose.  Look for the flare.''



``\emph{Message received loud and clear, Weaver},'' Tecton said.



I drew a flare from my belt and lit it, throwing it to the ground.



That done, I glanced over my shoulder at Rachel.  She nodded.



Jack's voice echoed through the complex.  I could sense him with my bugs now.  He was pacing back and forth, while all of the other Nine were stock still.  ``Attack the cities, target Scion, assassinate all of these powerful capes that are coming after me\ldots''



``\emph{Or} I could do all of the above.''



I hopped off of the dog's back to make it through the doorway, then ascended the spiral staircase.  The dogs struggled to follow, and I signaled for them to stop.



Couldn't have them blocking my retreat.



I wasn't sure what I could do, but there had to be \emph{something}.



I reached the top of the stairs, then stopped, my back to the wall beside the doorway.  I held my gun.



The sole remaining Cherish said something, a murmur.



``\emph{Weaver}.'' Jack said.  Screamer repeated the word after him, and it carried through the air, an echo.



``Hi Jack,'' I said.  I hung my head, focusing on what my power was telling me.



The bugs I had in the room clung to particular members of the group.  They were eerily still.



``Gray Boy is standing right in front of me,'' Jack said.



``I know.''



``Most are shut down.  Using a control to keep them still.  Too unmanageable in a group like this.  That doesn't mean you have the slightest chance of accomplishing something.''



``I have to try,'' I said, echoing Purity's words from the video.



``Such sad, small words,'' Jack commented.  ``You \emph{don't} have to.''



I had tricks prepared, but none of them were remotely viable.  Not with Bonesaw so close.



I would die, and she would revive Jack.  At best, I'd slow them down.



``You're too big for your boots, Weaver,'' Jack said.  ``You had a few critical successes and you've run with them.  Earned yourself a reputation.  But at the end of the day, you're still the same pathetic bug controller who got her powers because her \emph{mommy}\emph{died}.''



\emph{He likes to talk.  Every second that passes is a second we're catching up}.



``People probably said the same thing about you in the beginning, Jack,'' I said.  ``Too big for your boots.''



``They did.  My trigger event was a \emph{little} more dignified, though.  No matter.  I've been at this a long time.  You're barely a \emph{concern}.''



``Want to fight, Jack?'' I asked.  My bugs moved through the crowd as I noted each of the threats that were present.



``Eh,'' Jack said, shrugging,  ``I can take you.  Step through that doorway, and I'll give you a fair fight.  One on one.  Look.  I'll even put my knife in my belt, hands on my head.''



I had an assessment of their group.  I couldn't account for Nilbog's creations, but I knew which members of the Nine were present and where they were situated.



``You said it yourself,'' Jack said.  ``You can't afford \emph{not} to.''



Too true.  The others weren't close enough yet.



``Why this fixation on ending the world?'' I asked.



``Nuh uh uh,'' Jack answered me.  ``Not going to get bogged down in a discussion.  We have a \emph{situation.  }I'm going to walk away in about fifteen seconds, unless you want to have a \emph{duel}.  Knife against knife, or \emph{gun} against knife, if you prefer.  You win here, it's a coup for the \emph{world}.  What better option for the make-believe queen?''



The make-believe queen?



Maybe a name Cherish had given me.  I tightened my grip on the gun, but I kept my finger off the trigger.



Someone advanced.  I felt tripwires snap and break.



\emph{Letting a hostage go}?



I turned and started to fire before the individual in question could step through the doorway.  By the time I made the conscious decision and started squeezing the trigger, the individual in question was emerging.  The bullet made contact, passing through their head.



A life taken.  A hostage killed.  But I couldn't afford to take any chances.



No.



I shook my head a little.



A Nice Guy, not a hostage.



He needed to focus on people to use his power.  That focus was far weaker if he couldn't see someone.  My voice would be another vector, as well as knowing my location.



``That was impolite,'' Jack said.



``No tricks.''



``I could send Siberian after you,'' he said.  ``She wouldn't even have to kill you.  Just hold you still.  Bonesaw and Gray Boy could have worlds of fun.  Remember what we did to your team leader?  Imagine the eternity of pain Gray Boy could deliver \emph{after }our\emph{ }Bonesaw has given you more nerve endings to work with.''



``You could,'' I said.



The others were getting closer, reaching the foot of the stairs.



Cherish spoke.  ``The others are here, Jack.''



``Then your time is up, Weaver.  I hope you don't regret your hesitation.''



I wouldn't.



I drew in a deep breath, waiting for the second Jack turned, then stepped into the doorway.



Then I opened fire.



I'd first run into the scenario when I went up against Mannequin, before running up against Glory Girl.  The first time I shot a gun, I hit my target.



Now I had a better idea of why.



Having bugs over the entire area, I had a sense of the area, of the topography, of where everything was.  It wasn't perfect, but it was an advantage.  Something to help aim the shot, to help give me a sense of the path the bullet would travel.  It was like being able to reach out with my arm in a perfectly straight line, touch my target, then aim along the line.  The same effect I'd granted Foil, so she could snipe Tyrant.



The sole remaining Siberian moved to Jack's side before I could pull the trigger.



I wasn't aiming for Jack.  It wasn't even a consideration.  Like he said, he had Gray Boy with him.  The second I stepped into their sight, I was a goner.



My bullet took Cherish in the head.  Another bullet struck Screamer.



I hesitated.



Then I shot Aster, who was held in a Hatchet Face's arms.



Manton-



No.  Too dangerous.  Gray Boy was moving, trying to get to a better vantage point.



I turned, activating my flight pack for a boost of speed.



The Siberian broke away from Jack, giving chase.  Crawlers advanced only a pace behind.



In that same moment, I drew out more lines, giving the signal.



Revel and Foil both opened fire, their energy-orbs and bolts tearing through the walls and into the rank and file of the Slaughterhouse Nine.



``No!''  Jack ordered.  ``Siberian, with us.  The remotes are programmed?''



``Yeah,'' Bonesaw reported.



``We go.  Divide into groups.  One major target each.''



Jack quickly sorted them out, his Siberian touching him, Manton and Bonesaw as the bolts and orbs continued to tear through his crowd.  One or two dead every second.



And then they separated into groups.  Bonesaw paused, then broke away, joining her crowd before hitting the remote.  They disappeared.



Another group gone.



Then the remaining three disappeared all at once.



I collapsed on my hands and knees as I reached the bottom of the staircase.  The others that had managed to reach our location stood over me.



``They're gone,'' I said, panting not from exertion, but the sheer panic of what I'd done.



``We give chase,'' Chevalier said.  He looked to Defiant.  ``Can we?''



``We can if there is a computer,'' Defiant responded.



I only nodded.



``Good,'' Defiant said.



I looked up as Golem approached, Revel beside him.



``Aster's dead,'' I said.



He went very still.



``I'm sorry,'' I said.



``Did you--''  He started, then he stopped, staring down at me.



``Nevermind.  Sorry for asking,'' he said.  ``Whatever happened, it's for the best.''



He didn't sound like he believed it.  He didn't sound confident in the least.



\emph{It's for the best}, I thought, as Golem joined Chevalier and Defiant in heading up the stairs.



``Can you tell me the order they went off?''  Defiant asked.



I nodded.



``Good.  Then I think we can figure out which went where.  We can eliminate this place as an escape route.''



Which meant we knew which way Jack had gone, and he couldn't run anymore.



Final encounter.





