





Theo exhaled slowly.  He hadn't realized he'd been holding his breath.  Inhaling again, the smell of shit and blood was so heavy on the air it choked him.  His suppressed cough was almost a grunt, almost a gag.



His eyes returned to the two bloodstained spikes that had been stabbed into the wall.  It was the space where Nilbog had been crucified, apparently.  Something dangled from one of them.  A tendon, maybe, a vein, or a strip of meat.  The goblin king had been torn down with enough haste and enough force that some part of him had been left behind.



He'd spent some time staring at the metal spike with flesh dangling from it.  The others were busy.  It made sense to take the time to strategize, to get equipment and gear in order, familiarize himself with every tool and technique this squad of capes had on hand.



Thing was, Theo didn't want to, even as he knew it was the smart thing.  The others seemed to recognize that and weren't pushing him, weren't approaching.  Maybe they'd brush it off as a kind of meditative thinking, a mental preparation for the fight that was to come.  Maybe they'd see it for what it really was.  Avoidance.



Staring at the wall and trying not to think about anything was easier than looking \emph{down}, seeing the dead members of the Slaughterhouse Nine, and maybe seeing Aster in the mess of bodies.



Being silent was easier than having to look the others in the eyes and pretend he was alright, risking that they'd offer some gentle, kind condolences, and he'd have to be stoic in the face of it.



Men weren't supposed to cry.  It would be disastrous, shattering their image of him, creating too much doubt at such a crucial juncture.  He could imagine how they'd react.  Some of them would be awkward.  Defiant, maybe, would avert his eyes.  Bitch might say something harsh.



Revel, probably, would be nice about it.  Offer a pep talk, a hug, heartfelt words.  Tecton would be much the same.  Parian and Foil, even, might be kind, if he went by descriptions Weaver and others had offered of them and the little clues he'd seen in interacting with them.



The moment he pulled himself together, \emph{if} he could pull himself together, Chevalier would be at his side, all business, outlining the situation in clear, defined ways.  Framing it all into plans and setups that would put less stress on Theo, no doubt, but not in such a way that anyone could say anything about it.



Hoyden?  Hard to say.  She lived with this \emph{wall} that she'd erected around herself.  Layers of defenses, in bravado or being snarky or being sarcastic or aggressive or avoiding the situation.  In combat situations or real life, Theo suspected there were very few things that really got to the \emph{heart} of Hoyden.  When they did, they hurt.  How would she react to someone being vulnerable?



And then there was Weaver.



She was in the periphery of his vision, sitting on a computer case, staring down at the floor.  As ever, her mannerisms were peculiar.  She was so \emph{still}.  If it weren't for the bugs, or the fact that her head would periodically move, as if she were looking over the dead, he might have thought she'd stopped, like a machine with the battery removed.



She would be assessing who was dead, who wasn't, planning and adjusting her expectations for the coming fight, quite possibly.  Probably.



In the midst of that, was Weaver thinking about Aster?  The fact that she, either by aiming a gun and pulling the trigger or by giving the order to Revel and Foil, had killed a toddler?



Weaver was a hard person to deal with.



Taylor, not so much.



If that was all it was, he wouldn't have worried so much.



There were other possibilities, ones that troubled him.  What if he approached them, and nobody offered condolences at all?  What if they accepted it as a cost of doing business, a necessity in dire circumstances?



What if he \emph{did} show emotion, and none of his allies offered any emotional support at all?



Kayden had been the closest thing he had to a mother.  If it hadn't been for Jack's game, then Theo suspected he might never have rated.  He wasn't her first priority.  That would be Aster.  Not her second.  That was her \emph{mission}, nebulous as it had been in recent years.  He hesitated to believe that he'd even rated third place.



He struggled to convince himself he placed fourth or fifth, even.



But she'd been there.  She'd shown kindness, had stepped between him and Father when the situation demanded it.  There had been gentle moments, like the time they'd been watching television one morning and a cape had talked about how tinkers were their least favorite type of opponent to fight, and he and Kayden had \emph{laughed}, because Kayden and her group had run into Leet just a week before.



Stupid things, in the end.  Nonsensical.  But stupid, nonsensical things were sometimes the most important.



He'd never had friends, before he got his powers.  Even now, he wondered if he'd have really formed the friendships he had if they'd chanced to meet in some universe where powers didn't exist.



Being alone as often as he had, Theo valued the connections he had made.  Even connections with Justin, Dorothy and Geoff.  Crusader, Night and Fog.



On the flip side of that same coin, he felt the betrayal of Justin leaving him behind.



Above all, he felt the quiet, perpetual horror of knowing that Crusader was \emph{still} screaming, his throat never going raw, as Gray Boy's loop continued without cease.



Kayden would be standing a short distance away, stoic, trying to keep from slowly going insane as Justin's screams continued without end.



He'd lost people who were important to him, in maybe the most horrible way possible.  He'd lost his father, and Kayden, Justin, Geoff and Dorothy, and now Aster.  He'd lost them to violence and stupidity and madness, and he could see the allure in how the others seemed to be functioning, bottling it all inside.



He could see the twisted logic of it, even.  As if there was a binary to everything, every enemy was somehow a twisted mess of emotion, layered by a seeming calmness, while every ally seemed to be cold inside, with only an act on the surface.



He looked down at his mask.  A metal face with lenses over the eyes.  Stoic, expression neutral, or a little stern.  He'd chosen it at first because his real face was a little too round for a mask, but the PR teams had wanted to get more \emph{faces} on the team.  He'd compromised, and hadn't given his mask much thought beyond that.



Except time had passed, and he'd found himself wondering if he liked the message it conveyed.  By necessity, capes went down a road where they had to become cold and unflinching.  They had to become numb, had to inure themselves to hard decisions.  It jarred, to wear a mask that seemed to symbolize that transition, that while wanting nothing less than to walk down that road.



Back in Brockton Bay, New Wave had tried to start something, capes without masks.  It had been disastrous.  The message had been lost in the ensuing celebrity, and that had only intensified after one of the core members of the group was found and killed in her civilian identity.



He wondered if they'd been right to try.  If capes really needed to just\ldots drop the mask.  To cry and let the feelings out.  So many got their powers through trauma, but they bottled themselves up, erected defenses, developed coping mechanisms.  If New Wave's idea had taken off, would things be better?



Didn't matter.  Here they stood.



He could make it through this, save the world.  They could find the source of the Endbringers and defeat them, could clean things up, get things in order and stop all of the \emph{real} monsters\ldots he could go to college, get a career and find a girl and marry her, and at the end of the day, Justin would still be screaming.



Aster would still be dead.



The ugly decisions would have been made.



He stared up at the bloody spikes in the wall, an image that would be burned into his mind's eye, remembered as the point he stood at the threshold.  A mirror to where he'd been in the beginning, when he'd met Jack.



Bitch paced around the edges of the room, impatient.  She'd had to shrink her dogs to get them to an appropriate size, and was keeping them small in case the portal wasn't accommodating enough.  Here and there, she barked out orders to get the animals away from the bodies.



It grated.



``None of those invisible fucks,'' she said.



``Okay,'' Weaver answered.  Her voice was quiet.



Theo almost took her voice as a cue to reevaluate how she was reacting to what had just happened, then stopped himself.  Losing battle.  No point.



Then, for some bizarre reason, Bitch approached \emph{him}.



A sleek Doberman nudged at his gauntlet with its nose.  He looked down and then scratched it behind the ear.  It didn't matter if the dog bit him – he was wearing a gauntlet.



When he looked up, he could see Bitch staring at him.  Her face was barely visible behind her hair.



``Can I help you?'' he asked.  His voice came out harder than he intended.



She didn't seem to notice or care.  ``You're her friend, aren't you?''



\emph{I don't want to talk about Weaver.}



He didn't venture an answer.  He couldn't say \emph{yes}, not honestly, but he suspected Weaver had a different answer to the question.



``You're both acting different.  I can see it.''



``Kind of warranted, in this situation,'' he said.  ``In case you didn't notice, the last few members of my family just got killed.  I just need a bit of time alone to think.''



His voice had almost broken.  Couldn't break down.  Not like this, here, with her.



She hadn't taken his hint.



``They were buttholes, weren't they?  Purity and her gang.  The nazis.''



The dog nudged his hand again.  He gave it a more intense scratch before answering, ``White supremacists.  They\ldots weren't the best people ever.  But they were still my family.''



She kept looking at him, almost glaring.  She didn't answer or elaborate, leaving the conversation to die.



\emph{Go away.  I don't want to hit you}.



He kept silent, hoping she would just leave.  \emph{Willing} her to leave.



``Stay, Huntress,'' she ordered.



Then she walked away, leaving the dog at his side.



Theo scratched the animal under the collar, and watched it crane its head to one side, enjoying the contact.



It helped, oddly enough.  Having contact with another living creature without all of the issues and hassles of dealing with \emph{people}.  No judgement, no worries, just\ldots this.  Being alone without being alone.



His father had always preferred cats, and the creatures had never been easy to bond with.  This was nice.



Theo sighed.  He glanced at Weaver in his peripheral vision, and saw that there was a dog sitting next to her.  A mutt, at a glance.  The animal was resting its chin on her shoulder.



She saw him looking, glanced at Bitch, who was walking with her husky puppy following behind her, then shrugged.



He lowered his eyes from Weaver\ldots no, from \emph{Taylor}, then scratched Huntress again.



``We have the coordinates.  Waiting for a charge,'' Defiant announced.  He was already flanked by the Dragon's Teeth he'd brought with him.



``All gather,'' Chevalier ordered.



Bitch snapped her fingers twice, and her dogs returned to her.



Theo raised his hands to his face to rub his eyes, and he felt damp on one cheek.  One tear, fresh.  He wiped his face, glancing around to check if anyone had seen it.  No, not judging by the angle.



He donned his mask.



\emph{Golem now}, Golem thought.



``We need to decide who goes where,'' Defiant said.  ``The first teleportation marked coordinates on Houston.''



Weaver spoke up, ``I noted Shatterbirds and Burnscars leaving, some Damsels, bunch of others I didn't catch, but they had weapons and I'm thinking Winter or Crimson.  There were some I parsed as hostages, but it's only in retrospect that I'm thinking they were Nice Guys.''



``The second group made their way to New York.''



``Bonesaw and a captive Nilbog that's apparently rigged to create things on demand,'' Weaver said.  ``Crawlers, Breeds and a handful of others I didn't identify.''



Chevalier reacted to that, flinching.



\emph{His city, Golem thought.}



``And the last group headed to Los Angeles.''



``Jack's group?'' Golem asked.



``Yes,'' Weaver said.  ``He brought the Siberian, Hookwolf, Gray Boy, all eight Harbingers, and there are Psychosomas and Nyxes.  One or two others I didn't place.''



``Los Angeles?'' Chevalier asked.  ``What area?''



``\emph{That} area,'' Defiant answered, looking at the computer.



Chevalier nodded slowly.



Golem stared at the screen.  He could see the satellite image, the concentric circles that marked the area around the blinking blue dot.



``Charge prepared.  We can send one group at a time.  They've already got a twelve minute headstart.  It'll be another eight minutes before we can send the second group, eight minutes after that before we can send the third.''



``The first group to arrive can call for help and get support to the other locations,'' Chevalier said.



``Then why split up?'' Weaver asked.  ``We should \emph{all} hit Jack's group, trust others to help in New York and Houston.''



``Everyone else is closer to New York,'' Chevalier said.  ``But Houston\ldots''



``We can call in favors,'' Weaver said.  ``Moord Nag's apparently on board, though we don't know \emph{why}.  Cauldron's on board.  If we can get Tattletale in contact with them, that's \emph{handled}.  But we can't do that unless we \emph{leave}.''



``That's my city,'' Hoyden said.



``I get that,'' Weaver replied, ``But we're doing nothing constructive if we split up, and we're \emph{definitely} doing nothing constructive as long as we sit here.''



``Once we leave,'' Defiant said, ``We break the configuration cell and everything here breaks down on a Euclidean level.  There's no going back, changing our mind.''



``I get that,'' Weaver said, ``But two or three of us aren't going to do anything special.  We need big guns.''



Golem closed his eyes.



\emph{There she is.  }Weaver.



``She's right,'' Chevalier said, looking at Hoyden.  ``We'll send every set of reinforcements we can, but it's not worth what it costs us, to break up our group.''



``Shit,'' Foil said.



Hoyden had gone stiff, bristling for an argument.



``I'm \emph{not} saying we should abandon Houston,'' Weaver said, before Hoyden could speak.  ``Defiant, can you postpone the collapse of this area?''



``Yes, but I don't feel comfortable doing it,'' he responded.



``I think you should,'' she said.  ``Toybox left enough stuff behind.  Use it.  Stay behind, arm yourself, then throw everything but the kitchen sink at them.  You remember how the scar formed in Brockton Bay?''



``Mm,'' he said.  ``Tinker technology takes time to understand, to prepare.  Too dangerous otherwise.''



``There's a solution to that.  I'll point the way.''



Defiant hesitated.



Golem looked around the group, saw the expressions on faces, saw how even Hoyden had relaxed a fraction.  Even the Dragon's Tooth officers that accompanied them were a little more at ease.  There were no \emph{answers} in this situation, but there was a possibility.  An option, vague as it was.



``Okay,'' Defiant said.



Then, without so much as a farewell or a `good luck', he hit the enter key.



\sectionbreak



Golem appeared a full four feet above the ground.  He hit the ground and let his legs sink in, absorbing some of the fall.  A second later, he pushed himself out.



Just the use of his power gave him a sense of the area.  Touching the pavement gave him a sense of how all of the pavement around him was organized.  It had been folded into itself, folded around, thinned, thickened, bent at right angles.



Looking around, he could see how the buildings had been altered.  Textures had been removed, similar materials blended into one another, everything fortified, thickened, weaponized.



All around them, the buildings were like tombstones.  Windowless, angular, all expression and human touches removed from them.  Spikes studded corners and blocked alleyways, criss-crossed in front of doors, and carpeted pathways.  Some were metal, others camouflaged.



They'd figured out how to fight Tohu and Bohu during the Los Angeles attack.  The trick was responding quickly, stopping them before Tohu had her masks and Bohu managed her influence.  They'd \emph{won}, for lack of a better term, managing the fight without the casualties they'd seen in the prior attack, but they'd still lost a chunk of the city in the time it took them to beat and batter the towering Bohu into submission.  Now Santa Fe Springs and all of the neighboring districts were uninhabitable, due to the traps that riddled it, the way the infrastructure had been completely and totally compromised.



Easier to found a new habitable area than to try to fix \emph{this}, routing new pipes and power, managing traps both subtle and blatant.



Those same traps would be a problem here, but they weren't entirely incapable.  They'd dealt with this before.



Bitch's dogs grew abruptly, then shook, sending blood and bits of flesh and bone everywhere.



``HQ, come in,'' Chevalier murmured.  He continued to speak, delivering the information about Jack and the target areas.



``Area's empty,'' Weaver said.



``A trap,'' Golem responded.  ``Has to be.''



``Has to be.  Why else come here?''  Foil asked.



``Nyx illusions,'' Tecton said, ``He doesn't know we're aware of who he brought, so he's set them up to stall us.''



\emph{Nyx.  Her gas is concentrated into solid shapes that move at her will.  Break that shape and it becomes a cloud of poisonous gas.}



``Not that easy,'' Weaver said.  ``Maybe he knows we know, and it's a double-bluff.''



``Parian?'' Weaver asked.



Parian nodded.  She unfurled the bundle of cloth from her back, then quickly shaped it into a roughly humanoid shape.



A moment later, it was stomping ahead, forging the way.



Golem fell in step beside Tecton.  Every footfall on a surface concentrated his awareness, informing him of every surface of a matching material in the area.  Lightning flashes in his consciousness, showing the landscape around him.  He deliberately stepped on other materials to inform himself on concrete, on brick, on steel and glass.  His heavy boots made for a rhythmic sound, accompanied by the sounds of Chevalier and Tecton's own heavy footfalls, and the rougher patter of the mutant dogs.



``\emph{Stop}.''



A girl's voice, over the comm system.  Not Tattletale.



``\emph{Golem, tell them to stop.  Now}.''



``Stop,'' he said.



A second later, he wondered if he should mention this phantom voice.  A trick on Screamer's part?



``\emph{Thirty one,'' }she said.



``Thirty one?''



``\emph{More uses of my power.  I've been testing it, straining it, figuring out my limits.  I can't make promises.  Might be less.  Might be able to squeeze out more.  But it's the best I can give you.}``



The numbers clued him in, belatedly.



Dinah Alcott.



``\emph{There's bigger problems},'' she said.  Her voice was quiet.  ``\emph{In two minutes, everyone but you dies.  Seventy-two percent chance.}``



He stopped short.



``Golem?''  Hoyden asked.



``Solution?'' he asked, he raised a hand.



``\emph{Can you think in abstracts?''}



``Abstracts.''



``You're\ldots kind of scaring me, Golem my boy,'' Hoyden said.



``He's talking to someone in the comms,'' Weaver said.  ``Tattletale?  Not Tattletale.''



``\emph{Red means forward, left, attack, team.  Blue means back, right, retreat, solo\ldots I can only ask a certain number of questions a day.  Ask, I can narrow it down, but it's less help I can give later.}''



One keyword, and he had to figure out what option it led to.



``\emph{Blue, Tecton.}\emph{Retreat}.''



``Back up,'' he said.



Collectively, they retreated several steps.



A moment later, one small group of the Nine appeared, pushing their way through solid doorways, leaving colored smoke in their wakes.



Each was young.  Teenagers.  Each had a matching mask, a snarling face, complete with fangs and glowing dots in the dark eye sockets.  Their clothing flowed, with hoods peaking above their heads.  Each carried a different improvised weapon.  A fire axe.  A two-handed shovel.  A makeshift spear.



``Harbingers,'' Weaver said.  ``Don't let them get close!  Finish them quickly!''



``Color,'' Golem whispered.



``\emph{Blue}.''



He went with his instincts more than anything else.  ``Retreat!  Run!''



Parian's doll reached out, and the Harbingers slipped out of the way of the hands, dodging by virtual hairs as they spun in tight circles, ducked and rolled.  It was like the thing was moving in slow motion, but it wasn't.



A fire axe and two kitchen knives slid through the creature's body, severing seams.  It deflated explosively.



Foil opened fire with her crossbow, aiming so it was on a path to hit two of the enemies, and the Harbingers dodged the shot.



\emph{She's not supposed to miss}.



Tecton shattered the ground, but it didn't make the slightest difference.  The Harbingers didn't slow down.



They turned to run, belatedly.



Hoyden and Chevalier held their ground as others mounted dogs or took flight.  Golem ran his fingertips along the panels at his armor, feeling the connections to the various substances around him flare, touched the one for pavement.



He thrust his hand inside.  A small hand, emerging as fast as he could shove his hand inside the panel.  He reached for the closest Harbinger's foot.



The young villain pulled his leg up out of the way, virtually spinning as he stepped to the side, planted the same foot on solid ground, then resumed his forward momentum.  No luck.  It was like Harbinger could see it coming.



Weaver's bugs were swarming the Harbingers, but they took to spinning, relying on the movement of their hoods and the flowing black clothes to drive the bugs away, batting them aside.  Even the threads seemed to fail to do anything substantial, getting caught up in the approaching villains as they moved.



Like whirling dervishes, they closed the distance.



He thrust his hand into the pavement again, and this time, he created a platform like the one he'd fashioned in Ellisburg.  Raising them up off the ground, out of reach.



If there was any difficulty getting down and resuming their search for Jack, he'd deal with that when they weren't all about to be murdered.



The Harbingers scaled the sides of buildings as if they were running across horizontal terrain.  Weapons, fingers and boots found traction in the surfaces, and they climbed with an easy, almost eerie ease, as though they were almost floating.



Climbing faster than the hand was rising.



Three reached the top of the building, and as if they'd coordinated, planned this well in advance, they set foot on the edge of the rooftop and kicked off.  They ignored the bugs that plagued them as if they weren't even there, weren't binding them with silk.



They flipped heel over head, their backs to Golem, Hoyden, Tecton and Chevalier, the two Dragon's Teeth.  Rachel, Parian and Foil were on the dog's backs, and Weaver was airborne.



The Dragon's Teeth aimed containment foam at the three Harbingers.  The clones pulled off their flowing jackets with sleeves that almost covered their hands, catching the foam, then landed.  One swept the bundle of foam to try to knock a D.T. officer off his feet.  The officer hopped up, then struck out at the Harbinger clone.



\emph{No use}, Golem thought.  \emph{A mistake}.  Harbinger caught the arm, almost effortlessly turned around, pulling him in the direction of the turn.  A little push, and the soldier fell.



``\emph{He's okay},'' Dinah said.  ``\emph{Blue}!''



\emph{Run}, \emph{retreat}.  As if there was a place to go.



Two attacks struck in concert, a kitchen knife and a fire axe, and a heavy piece of Tecton's armor was decimated, one gauntlet ruined.



No use.



One more landed on the heel of the hand.



Revel opened fire with a dozen orbs, but the enemy avoided them with an almost casual ease.  She reprogrammed them, altering the orbs' properties, and this time they homed in on their targets.  The Harbingers dodged them, used the changed trajectories to lure them into nearly striking the D.T. officer and Chevalier.  She stopped, hanging back.



Chevalier swung his sword, pulled the trigger mid-swing to shoot at one Harbinger that stood on a fingertip of the reaching hand-platform.  Both attacks missed.



The Harbinger closest to him stepped close, almost casually, and drove a paring knife through a slit in Chevalier's visor.



\emph{His good eye}, Golem realized.



Nobody had figured out Harbinger's power, before Harbinger disappeared off the face of the planet.  It was an ugly reality that such questions weren't always answered.  The best guess suggested a hyperawareness of space and the movements of their own bodies.



But being able to figure out that Chevalier was half-blind, being able to blind his good eye?



One stepped close, holding a ball-peen hammer in each hand.  He closed on Golem, invading his personal space, until their noses were touching.



Golem tried to wrap the Harbinger in a bear-hug, felt only the faint drag of cloth against the metal of his gauntlets, empty air.  His intended target had ducked low.



He drove a knee forward.  \emph{Tight, contained movements}, give them as little to work with as possible\emph{.}



No contact.  Of course.



He was rewarded with a swat of the hammer against his mask, shattering one lens.  He'd thought he was out of reach, but the boy held only the very end of the hammer between index and middle finger.  He tossed the hammer in the air, letting it spin head over end.



Golem struck at the flying hammer, but another strike of the hammer caught his arm.  His fingertips fell short, and the handle of the weapon rolled over the back of his hand.  The Harbinger caught it, then thrust it forward in the same motion, driving the top of the hammer against Golem's nose.



``Don't kill him,'' another Harbinger said.



``I know,'' was the reply.



They didn't even sound \emph{winded}.



None of the others were doing demonstrably better.  The remaining D.T. officer was holding his own, but the others were being slowly, systematically beaten.



\emph{He's dragging it out.  They're making this into a game}.



No use letting this go on.



He retreated, only to find one Harbinger sticking a foot out, planting a foot on the small of his back.  He was pushed forward, then promptly struck in the abdomen.



Rather than try to defend himself, he tucked his chin to his collar-bone, let himself fall, and thrust his hands into the armor panels for pavement.



Double-thrust, one hand extending from the other, pushing Chevalier off the hand.



Another motion, simultaneous, to bring a hand of stone out of the wall behind Chevalier.  It emerged slower, but it formed a shelf, and Chevalier landed on that ledge.



The Harbingers could dodge, but his teammates were valid targets.



Another thrust, this time for himself.



Selfish, maybe, but he couldn't save anyone if they were interfering with him.



One struck at his leg as he launched himself off the hand.  It altered his trajectory, put him on a course where there wasn't anything nearby to catch himself with.



Two hands, into brick.  One connected to the other.  While they were new, he could move them.  Trouble with having them against the side of his body was that he couldn't get a full range of movement like he could get with his arms.  No matter.  He caught himself by the mask, then pulled himself closer to the building.



Another hand, another shelf.



Hoyden exploded, but the Harbingers didn't get hurt.  They spun, spreading the damage around like a person might roll to absorb a fall, ducking and sidestepping to put themselves at the periphery of the effect.



``\emph{Scion's closing in},'' Dinah said.  ``\emph{Blue, Golem.  It's still blue.  I can't use my power too many times today, but your numbers are getting worse and the answer keeps turning up blue.  Retreat, go right, go solo or go back.}``



``\emph{Someone needs to intercept Scion},'' Weaver said, over the comm system. ``\emph{We can't have him get involved.}``



``\emph{You go},'' Chevalier said.



Golem searched the sky, then spotted Weaver at the fringe of the battle, surrounded by a cloud of bugs.



She took off.



Golem grit his teeth.  \emph{More immediate things to focus on}.  He tried to launch Tecton to freedom, but the Harbingers intercepted him, driving Tecton out of the way in the same instant the hand appeared.



The D.T. soldier managed to deliver a glancing blow.  Golem couldn't tell if it was intentional or not\emph{, }because the hit was followed by the D.T. soldier being caught with a length of cloth wound around one wrist.



Tecton stepped in, drawing attention and striking out with his gauntlets, one damaged and one intact.  It bought the D.T. soldier some room.



Golem took the opportunity to launch the soldier to safety.



There were others on the ground, approaching.



\emph{One of these bastards could probably take us apart.  Eight of them, we can't hurt them, we're losing time, burning resources.}



Tecton glanced at Hoyden.  A communication seemed to pass between them.



They struck the palm of the hand, and the entire thing shattered.



Hoyden, Tecton and five of the Harbingers descended with a shower of rubble.



Hoyden and Tecton broke their fall with uses of their respective powers.  Hoyden hit the ground to generate an explosion.  Tecton punched the earth with his piledriver in the instant he reached solid ground.



The Harbingers didn't have that ability.  A five-story drop.  People had died or been seriously hurt after a \emph{three}-story drop.



\emph{Nobody told them that}.  In the midst of the thin cloud of dust and the chunks of debris, the Harbingers moved without wincing or giving any sign of pain, their black-clothed forms rising from the ground like spectres.



``Talk to me, Dinah,'' Golem said.



``\emph{Situation's getting worse.  Numbers are getting worse, across the board.  I'm not asking any specific questions, but I can sense it, just\ldots the big picture.  It's not working.}``



\emph{There's an answer here, and we can't see it}.



``Blue\ldots Backwards, go right, retreat, solo?  What's that last one?''



``\emph{Abstracts.  Nothing specific.  It's only as meaningful as it helps you come to the right decision.}''



He stared at Hoyden and Tecton, surrounded by the eight Harbingers.



``If I leave\ldots how does that change the numbers?''



``\emph{Success}.''



``Chances for Tecton and the others?''



``\emph{Better than they were.}''



This was hell, Golem mused.  This was the nightmare that had driven Weaver from her home city, drove her to surrender.



The right path, but god damn, did it look ugly.



He bit his lip, then formed another pair of connected hands to launch himself skyward.  He reached the apex of his flight, then created a shelf to land on.  He did it again, and this time the shelf he created was just at the edge of the roof.  He stepped over onto the rooftop, then broke into a run.



``Saving Tecton, red or blue.''



``\emph{Golem, we didn't get a chance to go over this earlier, but you need to know\ldots I can't ask that many questions}.  \emph{I've been saving my power for the last big confrontation.  Tattletale said this is the time to act.  I used my power twice to answer big questions earlier today.  Another three to figure out who I needed to talk to, and that told me-}``



``I'm the best partner for you?''



``\emph{Right now, yes.  Listen.  Twenty-six questions left.  We haven't even found Jack.  I can't figure it out.}``



He stood on the rooftop, then extended his arms out to either side.



She couldn't read his mind, so it was only identifying options.  Everything to the left of his nose was blue, everything to the right was red.



``Red or blue.  Now.''



``\emph{Blue.  Twenty-five.}``



``Jack's to my left,'' he said.  He turned ninety degrees.  ``Again.''



``Blue.  I'm-  My power's getting fuzzier.''



\emph{Scion}.



He looked up at the sky.  Weaver with her swarm was there, forming a great wall across the sky, as if to draw attention to herself.  Scion was approaching, a ray of golden light streaking across the overcast sky above.



Scion shut down precog abilities.



He felt something knot in his stomach, an ugly feeling, ominous.



``Let's get as much use out of it as possible.  Saving Tecton and the others\ldots Red or blue!''



``Red.  Twenty-three.''



He hesitated.  ``It's not me going back?''



``No.  I don't think so.  I just asked and it said no.''



\emph{Break it down.  Attack, left for blue.  Group, forward for red.  }``Again.''



``Golem, we can't waste questions like this.  We-``



``Please.''



``Red.''



\emph{Group or forward, }he thought, assigning colors to each option.  ``Again.''



``Blue.  Somewhere between eighty and ninety percent chance.  I- I'm going blind here, Golem.''



\emph{Group}.



Group, but not returning to join the others?



He went with his gut.



``Tattletale, are you listening?''



``\emph{Yes}.''



``Reinforcements.  Call in the big guns.''



``With Jack close?  That's against the quarantine.''



``Dinah, does it improve our chances, \emph{everyone's} chances, as far as this end of the world scenario?''



``\emph{Yes.  A lot},'' she sounded genuinely surprised.  ``\emph{Twenty}.''



``\emph{Cauldron's refusing aid,}'' Tattletale said.  ``\emph{They said it's because Scion's presence is blocking their clairvoyant.  They're lying.}``



High above, Scion reached a stop, hovering in front of Weaver, who hung in the air in turn, using her flight pack.



Golem tore his eyes away from the scene.  He glanced down at the street, where Bitch, Parian and Foil were reinforcing Tecton and Hoyden, backing them up as the Harbingers approached.  One Harbinger threw something, and a dog dropped like its heart had stopped.



He shook his head.  He could watch forever, but they were better served by having him elsewhere.



The sooner he got Jack, the better.



``Jack is southwest of my location,'' he reported.  ``Heading off solo on precog advisement.''



He bolted, running.  His power bridged gaps between buildings.  He set his foot down on the corner of one rooftop, then vaulted himself over a trap that he sensed just a foot in front of him.  His landing jarred it into motion, provoking a deadfall, a slice of building that toppled and dropped onto the narrow street below.



Another hand broke a row of spikes that lined the edge of another rooftop.



Once, he'd been fat.  Once, he'd been out of shape.  Two years and a mission had given him the chance to remedy that.  He wasn't conventionally fit, still had a bit of stockiness to him, but the fat was gone.  He had muscle.  Running with Weaver had made this doable.



Twenty more precog answers.



``Numbers if I stay on the rooftops?''



``\emph{Twenty to thirty percent chance of injury or being taken out of action.}''



``If I'm on the ground?''



``\emph{Fifty-something.  Eighteen questions left.}''



Her numbers were getting less accurate, the picture of the situation cloudier.



Too many powerful individuals in the area, too many chances of disaster, too many unknowns.



He set foot on one rooftop that had changed less than most, and the lightning flash was a staggered one, as his feet first touched gravel, then the material of the rooftop \emph{beneath }that gravel.



The next rooftop wasn't made of either material.  It wasn't made of brick or concrete.



He created two hands, chaining them together, and extended the hand into the building.



It detonated into a massive cloud of smoke.



He launched himself away to avoid it, but it wasn't enough.  The smoke flowed towards him like a wall, too vast to avoid.



Too vast to avoid so long as he remained on the rooftop.  He shoved himself off, created more hands to form a series of ledges that might serve as a staircase.



The smoke still loomed.



He got as close to the ground as he could, then launched himself to safety.



Golem was panting as he rested on the ground.  Psychosoma's monsters emerged from the smoke, one using the same ledges he'd created to descend, the other crawling on the outside of the building.  Homeless, to look at them, twisted into monstrous shapes.  False shapes.  He could deal enough damage and break the effect, and they'd be human again, unhurt.



Simpler than it sounded.  If he broke the effect for one, the other would tear the freed victim apart.



Golem rose to his feet, backing away as swiftly as he could.  He was out of reach of the smoke, but these \emph{things}, they were a distraction, a speed bump.



He waited, dropping into a fighting stance as they approached.  They broke into runs, charging him blindly, two figures so thin they didn't look real, their fingers and feet twisted into claws as long as his forearm.



They plummeted into a pit in the middle of the road.



Golem rose from the fighting stance, then hurried on.  His footsteps continued to mark the surfaces around him, making it clear where there were more of Nyx's illusions, more traps left over from the Tohu-Bohu attack.



His other enemies wouldn't be so gullible.



``Left or right?'' he asked.  He had a mental map of the surroundings.



``\emph{Left.  Somewhere around a ninety percent chance Jack's in that direction}.''



Each question narrowed down the possibilities.  From fifty percent of the area to twenty-five percent, then twelve and a half percent\ldots now six percent.  It was a small enough slice that he didn't need to wonder as much.  If he kept on this course, he could find his target.



``\emph{Right route},'' Dinah said.  ``\emph{It's\ldots it's really fuzzy, but I still feel like the bloody, ugly ends aren't so close.}''



``A good feeling,'' Theo said.



``\emph{In a numbery way.}''



A numbery way.



``Status,'' he said.  ``Not a question.  Just\ldots I need to know what's going on.''



``\emph{The others are\ldots okay},'' Dinah replied.  ``\emph{Defiant just arrived in Houston with a giant robot that only has one arm and one leg, and we've got}\ldots''



Dinah's voice continued, but he didn't hear it.



Golem slowed to a walk as he saw his new surroundings.  The tombstones of Bohu's area were still here, but they were \emph{scarred}.



A thousand times a thousand cuts.



``Theodore,'' Jack said.



Jack emerged, and he wasn't holding a knife.  He held a sword, nearly four feet long.  \emph{A claymore}.  His shirt was unbuttoned, showing a body without a trace of fat.  His beard had been meticulously trimmed, but that had easily been a day ago.  His neck had scruff on it.  Strands of dark hair fell across eyes with lines in the corner as he stared at Golem.



Golem had gotten this far.



Now what?



Jack let the blade's point swing idly at calf-level, pointed off to one side.  Cuts gouged the road's surface.  Theo let his fingers trace the panels on his armor.  Steel, iron, aluminum, woods, stone\ldots



His second sense marked various items in the surrounding area that were made of the same substance, even marked the trap off to his left, but it didn't touch any part of the sword.



``All on your lonesome,'' Jack said.



``Yes,'' Theo answered, sounding braver than he felt.



His finger touched other panels.  Brick, asphalt, concrete, porcelain\ldots



The sword remained out of his power's reach.  He'd put so much stock in being able to disarm Jack.



With each contact, he felt the accompanying flashes, tried to put together a mental picture of his surroundings.



Two false building faces, just a little ahead of him.  They had to be Nyx-made.  If he advanced, she'd break the illusion, and he'd be surrounded in the noxious smoke.  At best, he'd pass out.  At worst, he'd pass out and wake up to permanent brain damage and organ failure.  Or being in the clutches of the Nine.



Jack let the sword swing, and Golem tensed.  The blade didn't come anywhere close to pointing at him, but Jack's power cut shallow gouges into the surrounding brick, stone and pavement.



``Alone,'' Jack said, again.



\emph{Because of you}, Golem thought.



He clenched his fist.



Tears were forming in his eyes.  Ridiculous.  Wasn't supposed to be what happened in this kind of situation.



Jack, in turn, smiled slowly.  ``Quiet.  I was thinking that after all this time, we could have some witty banter.  You can scream your fury at me, curse me for killing your loved ones.  Then you do your best to tear me apart.''



``No.''



``Oh!'' Jack smiled wider.  ``Show mercy, then?  Walk away from the fight and show you're the better man, rather than descending to my level?  I've been waiting for someone to pull that ever since I saw it happen in a movie.''



``This isn't a movie.''



``No.  It's very, very real, Theodore,'' Jack said.  He paced a little, letting the sword drag on the ground.  The blade was white, Golem noted.  White, exceptionally sharp.



Mannequin-made?



Or was this Jack an illusion?  Nyx could imitate voices.  She could create the gouges in the walls by way of the illusory smoke.



Golem paced a little too, mirroring Jack's movements.



``Well, I'm not sure what you expect, then, \emph{Theodore}.  The fat little boy promised me he'd become the kind of hero that would put down monsters like me.  I gave you two years, and you've made it at least partway.  Did you change your mind on the killing part?''



``No.  I will kill you.''



``So tough!  So brave!  All of this from the--''



``\emph{Stop talking}, Jack.  You're not that clever, not as sharp as you like to think.  You talked to me about keystones?  Bullshit.  You're a sad, pathetic killer with delusions of grandeur.''



Jack's smile dropped from his face.  He held the Claymore with one hand, the blade's point touching the ground, and spread his arms.  His unbuttoned shirt parted, showing the whole of his bare shirt and stomach.  Showing himself to be vulnerable, exposed.



``Then do your worst, Theodore.  Because if you don't, \emph{I }will.''



``\emph{Dinah},'' he whispered.



``\emph{With you.  Gray boy isn't near.  Nyx and Hookwolf are.  Fifteen questions.  I had to use one to help the others.}''



He nodded slowly.



\emph{I don't like the illusory building faces.  }Too much poisonous smoke was needed to make that sort of thing, it had to be multiple Nyxes working in concert.  They'd be close, probably.



Which said nothing of the other threats that loomed behind the fog.  Psychosoma's creations?



Golem reached up to his gloves, then tore off the protectors on his knuckles.  They fell to the ground.  Beneath were spikes.



``Nice touch,'' Jack said.



Golem spread his arms.  ``What do you--''



``\emph{Red}.''



Mid-sentence, still talking, he let his arms fall, driving them into panels at his side.



Jack hopped back out of reach of the hands, seizing his sword.  He drew it back.



``\emph{Blue}.''



Golem created another hand.  Not to catch Jack, but to catch the blade.



It had backfired, if anything.  The hand caught the tip of the blade, but the sword slid free of the grip and flew around with \emph{more} force.  Golem leaped back, letting himself fall, and let his feet slide into the pavement.  Two boots rose from the ground, shielding him as the slash caught the surface.



Weaver's lessons.  Catching the enemy off guard by any means necessary, rolling with the punches, or rolling with the effects of the enemy's attack.



Had to use Dinah's ability, divide everything into two equally viable actions, so he wasn't caught off guard.



Still prone, still shielded and out of sight, he reached into the ground with both hands.



Two hands, flattened, jabbed for Jack's leg, stabbing at ankle and calf.  Jack backed away again before they made contact, slashed again.



This time, the slash caught a section of Golem's armor that was sticking out of cover.  The cut made a mark nearly a foot deep in the ground, but it served only to split the pauldron in half.  A section of metal fell to the ground.



He created two connected hands of pavement, then whipped them to throw the section of pauldron at Jack.  The trajectory suggested it would fly a little to Jack's left.



Golem jabbed one hand into the ground, and a flattened hand stabbed out from the spinning piece of metal, extending as the projectile flew.



Jack ducked, but Golem was already thrusting his other hand into the earth.  It jutted from the hand he'd created, doubling the length in short order.  More of a crude boomerang in shape than a chunk of metal.



It only clipped Jack, just barely.



``Clever boy,'' Jack said.  ``You--''



``Stop talking, Jack,'' Golem responded.



\emph{For Aster, for Kayden, even for the others\ldots}



He thrust his hands into the ground, repeatedly, and they stabbed at the underside of Jack's feet.  He leaped back out of reach and swung his sword the instant he touched ground.



The action cut through the remainder of the shield Golem had raised, but it also kept Jack in one place.  He caught the underside of Jack's foot.  Jack stumbled as he pulled himself free of Golem's grip.



He reached out to stab out with two interconnected hands, the same technique he used to launch himself.



But Jack evaded it, slid out of the way, almost as if he knew the strike was coming.



Golem moved to get into a position to strike again, and realized in the moment that it would take too long.



He was crouched, still, his hands remained buried, and Jack was already drawing his sword back.  He couldn't mount a defense in time.



He braced himself.  With luck, his armor could take it.



The attack didn't come.



No.  Jack laughed, instead.  His icy blue eyes were fixed at a point beyond Golem.



Golem chanced a look over his shoulder.



He saw a figure dropping out of the sky, trailed by what looked like a comet's trail of black shapes.  Weaver.  Her course changed as she flew away, using the Bohu-warped buildings for cover.



And where she'd been, just moments ago, a dull gray light hung in the sky.



Scion.  Trapped in Gray Boy's time-well.



Jack's laugh rang through the area.



The figure inside moved, but only barely.  The well trapped powers within.  Kayden's lasers wouldn't exit the area.  Crusader's duplicates wouldn't be able to wander beyond the well's limits.



And Scion didn't appear to be any different.



``I'm sorry, my boy,'' Jack said.



Golem whipped his head around.  Jack had backed up a short distance.



Jack chuckled, as if he still found something funny about the situation.  ``Ah well.  I'm disappointed.  I'm not sensing it, your killer instinct.''



``I'm prepared to finish you,'' Golem said.



``You're prepared?  Maybe.  But not practiced.  No.  I don't see this going anywhere interesting.  It's about the ripples.  You remember our conversation?''



Theo nodded slowly.  \emph{The ripples from a butterfly's wing.  The effects that extend out from any event. }



``You?  \emph{This}?  It's nothing.  What ripples extend from this?  You're \emph{weak}.  That?'' Jack pointed at Scion, trapped in the sky.



Golem chanced another look.  Nothing had changed.  Scion remained fixed in place.



``\emph{That} interests me.''



He climbed to his feet, eyes on Jack's weapon.



Jack reached into his belt, then drew a knife.



Golem tensed.  Faster than the sword, if not quite so capable of chewing through his armor.



But Jack didn't attack him.  He struck at the building faces.



The surfaces dissolved into rolling clouds of smoke.  Golem vaulted himself back twice in quick succession to escape it, then continued to back away for good measure.



``You've failed to amuse me.  A shame your sister's been shot, and there's nothing interesting to do with the hostages,'' Jack called out, his voice ringing along the length of the street.  With no details or features on the outsides of the buildings Bohu had altered, the voice carried in an odd way.



A shadow emerged.  Jack, riding atop a massive six-legged beast.



As Jack approached, he became more visible, and the nature of the beast became clear.  He stood on Hookwolf's back, between the creature's shoulders.



Other shadows appeared in the mist, and they, in turn, clarified as they approached.  Crawlers.  Mannequins.  Crimsons.  Others.



\emph{Done in by my dad's lieutenant}, Golem thought.  No way he was walking away from this.



``I suppose we'll kill you,'' Jack said.  ``And you'll just have to take me on my word when I say I'll find something suitably horrific to do as punishment for your failing our little game.''



Theo raised a hand as a shield even before Jack used his power in conjunction with Hookwolf's.  A hand of pavement, struck by a thousand slashes in a matter of a second, whittled to nothing.  Then he had only armor, and that, too, started to come apart.



The cuts that followed parted flesh.





