





The house was bustling with activity, even this early in the morning.  Ten children, aged four to seventeen, were doing their utmost to get ready for their morning activities.  It was a rule, that everyone had to keep busy.  A way, really, for the Gails to have a \emph{chance} to breathe.



``You all set?'' Mr. Gail asked, looking at him.



``Yeah.''



``Need a ride to your co-op?''



``No.  Takes about as long to take the bus.''



Mrs. Gail smiled.  ``Thank you, Theo.''



He shrugged, feeling awkward.  It had only been a few nights ago that she'd brought him an ice cream sandwich, something she hadn't done for the other foster kids the Gails were looking after.  She'd thanked him `for being one of the easy ones'.



He hadn't eaten the ice cream sandwich.  Getting fit was too important, and it was already an uphill battle.



Still, it had been nice.



As he'd started habitually doing, he took time in front of the mirror to check his appearance before making his way out the door.



It was all too surreal.  Endbringer attacks every two months, punctuated by periods of mundane life and intense, focused training.  Life continued as normal, with just a little more fear.  It wasn't the reaction he might have expected, but it \emph{was} a reaction.  Everyone was a little different, animated, as though they sensed the encroaching danger, the ominous, inevitable end.  Just like one person might react to a near-death experience with a new gusto for life, society as a whole reacted to each Endbringer attack.



Not \emph{celebrating}, not with the inevitable death tolls, but perhaps breathing a collective sigh of relief.



In a way, Theo mused, people seemed to sense that there was a dark cloud on the horizon.  Beyond even the Endbringers, there seemed to be an unspoken acknowledgement that things were well beyond their control.  That this thing with capes and parahumans wasn't going to turn out alright.



The illusion built up around the whole `cape' thing had broken, but people weren't talking about it.



Surreal, as though everyone was spending more time pretending than they were spending focused on reality.



Odder still, that he'd been one of them.  He'd \emph{grown up} with the reality of what happened when powers came in contact with the people who shouldn't have them, but he'd pretended.  He'd wrapped himself in delusions and false assurances.



Getting off the bus, he arrived at the PRT building before many of the employees.  It was easier that way, because it meant he didn't need to go through all of the usual precautions.



Taylor was awake when he arrived, her hair damp from a recent shower.



``Want to run?'' she asked.  She was already stretching her arms.  She had little enough body fat that the muscles stood out in her arms and shoulders.  Her long black curls were tied back into a loose ponytail, with some strands already slipping free to frame her face.



Muscles or no, she was still narrow, still tall.  If he didn't know her, and if the situation called for it, he might think he could take her in a fight.  Building muscle came easily to him.  Building fat did too, unfortunately, but the end result was that he was physically imposing, even at sixteen.



Yet if they scrapped, he suspected he'd be left crumpled in a heap on the ground.  It was the way she fought.  The way she \emph{thought}.



``If it's okay with you,'' he said, ``I was kind of thinking I wanted to do some sparring first.''



She didn't give any indication that it bothered her.  ``Sparring's fine.  You'll be sore for the run, though.''



He shrugged.



``Well, maybe that's good, learning to exert yourself when you're hurting and tired.  Stretch well, though.  We don't want you to lose more time to any injuries.''



He winced.  Few things set him back in his fitness regimen like a twisted ankle or stubbed fingers.



``Yeah.  I'll stretch after I've got my stuff on.  Meet you in the gym?''



``Sure,'' she said.



He was about to leave and do just that, but Taylor spoke up.  ``Theo?''



``Yeah?''



``Are you still getting anything out of this sparring?  We've come up with techniques, you're stringing them together, but there's only so much you're going to learn from me.  You might be better off working with the others.''



``I'm\ldots no.  I'd like to keep sparring with you.  I'll let you know if I don't think I'm getting anything out of it.''



She nodded.



All business.  Hard.  So focused she was almost cruel, at times.



He left, heading to his quarters to collect his gear.



Spider silk bodysuit on.  Heavier weave fabric over that, followed by the armor, which went on in layers.



The weight of it was a comfort.  It was familiar, just a touch musty.



There was a knock on the door.  ``Theo?''



Theo turned, then opened the door before returning to his armor.  He tested where the panels at his hip were placed, then adjusted the position on the belt before locking it in place.  ``What's up?  You're here early.''



``Had a thought on the suit last night, knew I had to come in early to implement it or I'd be distracted all day, trying not to forget about it.''



Theo smiled.  ``Tinker life is hard.''



Tecton chuckled.



``So you just wanted to say hi?''



``No.  There's something else,'' Tecton said.



Theo strapped on his pauldrons.  They consisted of more panels, and in a pinch they could be strapped to a point on his side or at his hip.  Backup, in case others were removed.



``I guess it's kind of like the armor tweak thing.  I've got to bring this up now or I'll never be able to find the right time, or I'll forget, or whatever.''



``It's serious?''



``Serious-ish.''



Theo turned, giving Tecton his full attention.



``It's come up with the others, because there's been points where things got uncomfortable, awkward, and we had to talk.  You're the only one I haven't discussed it with.''



``Weaver?'' Theo guessed.



``Weaver.''



``I think I can guess where this is going.''



``She pushed Cuff a step too far, back when we went after Topsy.  It worked out.  Grace found herself at odds with Weaver when we went up against Deathadder.  There were hard feelings for a bit after that.  I don't think Weaver knows she's doing it.''



``I think she knows,'' Theo said.  ``I don't know if she \emph{cares}.''



``That's not better.''



``Wasn't saying it \emph{was}.''



``Listen, Theo.  I'm not going to tell you to stop being her friend--''



``Is that what you told the others?''



``No.  But she isn't exactly buddy-buddy with anyone else on the team, is she?''



``She's not good at making friends.  I'm not either.  I get what you're saying.''



``I hope so.''



``But we came from the same city.  We've got common background.  And we're maybe the only people who are buying into this end of the world thing.''



``That's- that's \emph{good}.  That's fine,'' Tecton said.  He didn't manage to sound convincing.  ``But\ldots''



\emph{Of course there's a but}.



``\ldots{}I can tell you, she pushes herself hard.  We've all seen it.  She expects everyone to match her in that, up until you demonstrate you can't.  She'll back off then, but\ldots that's not a guarantee that there won't be some permanent damage.''



``Permanent damage,'' Theo echoed his team leader.



``Physically, emotionally.  Or even to your relationship with her.  I hate to put you on the spot, but\ldots do you like her?''



``As a friend, sure.''



Tecton didn't respond.  He waited.



Theo shifted his weight, felt the armor at his shoulder shift, and turned his attention to adjusting the clasp.  It made for an excuse to break eye contact.  ``Nobody else is here, right?  Nobody's going to overhear from the hallway?''



``Just me and you.  I ran into Weaver as she was heading upstairs.''



``She can hear through her bugs.''



``I know.  I asked her not to listen in.  I'm going to hope she won't breach that trust.  And if she does, if she \emph{is} listening, then maybe hearing what I just said will be a wake-up call for her.''



Theo nodded.  He ventured, ``A little.''



``A little wake up call?''



``No.  What you were saying.  I like her a little.  But that's not really me and her.  That's me being a big enough loser that I fall in love with any girl that spends more than five minutes with me.  We wouldn't work out, I know, because I \emph{know} how hard she can be to get along with.''



``You're not pursuing anything?''



``If I like anyone, it's Ava.  But she has the boyfriend--''



``Not anymore.  It was another point of contention, Weaver keeping us so busy she couldn't maintain a personal life.  We've\ldots geared down on that front, made sure we had downtime, but that didn't fix the rift in her relationship.''



``Oh.''



There was a pause.



``Wait a while before approaching her,'' Tecton said.  ``You'd make a good pair, and I think you're both nice enough you'd make it out okay after a breakup.  Anything more, anything that happens after this, do your best to convince me and the bosses it isn't happening.''



Theo nodded.



``But on the subject of \emph{Weaver}, I don't think it would be nearly as good or welcome.  I'd even recommend you back down.  I can arrange training schedules with the others, if you want to maintain your regimen.  Work on your versatility.\emph{``}



``I appreciate the offer--''



``--Hear me out,'' Tecton said, raising one gauntlet.  ``You like her.  Maybe you're a little in love with her.  That's normal.  I've been there, had that phase where I fell in love with girls really easily, 'bout a year ago.  I'm glad I came out of it in one piece.  So to speak.''



Tecton laughed a little at that, self-depreciating.  Theo smiled in sympathy.



Tecton continued.  ``But there have to be times you're\ldots not so keen on her.  You said it yourself.  She's hard to get along with.''



``Yeah,'' Theo said.



``I'm worried that if this training continues, a rift will form.  You'll stop being able to function as a team.''



Theo nodded.  ``I understand where you're coming from.  I do.  But\ldots''



``But you're going to keep doing it.  The training.''



Theo only nodded.



``Good luck, then.  I should get going to school.''



``Later, Everett.  Thanks for being straight with me.''



``Later, Theo.  Patrol tonight.  You and\ldots Cuff?''



Theo smiled, shaking his head a little.  ``Sure.''



With that, Tecton was gone, his heavy boots making surprisingly little sound as he walked over to his own quarters to remove the armor.



Theo prepared the rest of his armor, leaving the mask off, and walked briskly over to the gym.



Weaver was already in her full costume, framed by a half-circle of bugs.



``Done?'' she asked.



``Yeah.''



``Everything okay?''



He nodded.  ``Yeah.''



``I was thinking you should work on your vaults with the hands chained together.  If you--''



``Full contact,'' he blurted out the words.



She stopped.  ``Sorry.  I should have asked.  Seems like you know what you want to do, already.''



``I do.  Yeah,'' he said.  ``You against me.  A real match.''



She nodded.  ``This have something to do with your talk with Tecton?''



``Yeah.  But not like you're thinking.''



``Alright,'' she answered.  Her bugs shifted position.



It was a signal.  Theo let himself settle into a better fighting pose, hands close to the panels.



She didn't fly for cover.  She didn't move further away from the surfaces of the ground, walls or ceiling.  She made a beeline straight for him, flying low to the ground.



He created hands, but she reacted with an inhuman quickness.  A fault of his power, that it was so easily telegraphed.  Kaiser wasn't so unfortunate.



But that wasn't the entirety of it.  Her bugs crawled on the ground's surface.  She felt their movements like she felt a touch on her own body.  The moment a hand started protruding, she \emph{knew}.



Bees, wasps and cockroaches settled on his armor, covered his lenses.  He shook his head to clear his vision, saw her fly right between his legs, turning her body to slip through the gap.



He turned, felt a hand on the side of his head, a pull that capitalized on his shift of balance.



He looked up just in time to see the lights of her flight pack go dark.  She let herself fall, settling one knee on his shoulder, the other at the space where his shoulder joined his neck.  Over a hundred pounds of weight settling on top of him while he was off-balance, disoriented.



He fell, and she leaped off him, out of reach.



\emph{Roll with the attacks, use them.}



He let his chest strike the ground, his arms sinking into the ground.  He reached.



But she was too quick, already reacting.  She positioned herself on the battlefield, not behind him, not on either side, but \emph{above}.  Forcing him to look up, disorienting.  A slight shift of position forced him to turn around to keep her in sight.  A \emph{failure} to keep her in his sights saw her darting close to strike, to knock him off-balance.



And that was \emph{her}.  The bugs were massing, looping threads of silk, biting and stinging.



Short of her refusal to deal permanent injury or kill him, she barred no holds, showed no mercy, offered little kindness, if any.  There wasn't a thought to his morale, to the fact that she was systematically, methodically destroying the confidence he was building up.



No.  Not heartless, not wholly inconsiderate.  She tore him down because she trusted him to pull himself back together, to rebuild that lost confidence and redouble his efforts.



Nevertheless, this was one of those moments where he found himself hating her a little.  His fondness for her shrunk a fraction.  He felt, even though he'd asked for this, the slightest sense of betrayal.



Nothing Tecton had said was new.  He \emph{knew} this stuff.  Knew that walking down this road and continuing this training was going to hurt things between himself and Weaver in the long run.  Somewhere along the line, their friendship would suffer.  They'd dial up the seriousness of what they were doing, focus more on business than friendship.



He knew.



\emph{She} knew.



Weaver caught his legs, flying between them, catching his knees in the crooks of her elbow, dropping him onto his back, \emph{hard}.  He was already feeling trepidation at the run they'd scheduled for after this.  It was going to \emph{suck}.



But it was necessary.  If she could just impart \emph{one }useful lesson, it could make all the difference.  Some technique, some of her ruthlessness\ldots \emph{something}.



Anything would do.



\sectionbreak



Hookwolf's storm of blades had been augmented to an endless range, the strength of the cuts, thrusts, slashes and stabs augmented a fraction by Jack's power.  It didn't make the cuts more severe, but only extended the strength and severity of the cuts to the peak point in the blade's movement.  Heavy armor plates were scarred, cut and torn away.  The wounds to Golem's face, arms, chest and legs were different, the pain oddly delayed, as if it took time to sink in.



``\emph{Blue.}''  The voice sounded so far away.



It was the push he needed.  He twisted around, very nearly collapsing in the process.  The blades scarred the armor at his back, and precedent suggested it wouldn't last more than a few seconds.  It was a chance to move.  To run.  He'd have time to run, to get to the nearest alley, before the armor was shredded.  He could use his power to block it off, to buy himself time, contact the others\ldots



All he had to do was put one foot in front of the other.  Get away first, then attend to the rest.



His foot raised off the ground, and as if he were walking through a doorway that marked the point between reality and a dream, he felt the strength go out of him.  He felt red-hot pain that seemed drastically out of proportion for the small areas it was concentrated into, all across his front.  Felt warm, damp blood in his boots, squishing between his toes in their spider silk stockings.



The shock of it was the worst part.  Stunned, unable to shift mental gears, Golem collapsed.  The pain was worse, as he landed flat on his stomach.  He let out a guttural groan, mingled with despair.



Too hurt, too damaged.



``\emph{I'm sorry, Theo}.''



The last words he'd ever hear?



He waited for the end to come, but Hookwolf had stopped.



``This is the point where we have a long talk, Theodore,'' Jack said.  ``So I've had Hookwolf ease up on you.  You can bleed out while I taunt you, and maybe I talk about what I could do when we revisit your stepmother.  Gray Boy is the only person who may be able to touch her, but that doesn't mean Bonesaw can't give him a few things.''



Golem's fingertips scraped against the surface of the road, as if he could find some kind of traction there.  When that failed he clenched his hand into a fist.



``It's my favorite part,'' Jack said.  ``Except\ldots you're clearly not interested.  \emph{Stop talking, Jack}.  Which means we skip right to it.''



Golem couldn't see, but he felt it as Jack struck him.  Not Hookwolf's blade, but that damn sword.  It hit him in the side, shearing through the metal of his armor, stopping at the reinforcing struts and spider silk armor beneath.  The force of the blow was enough to flip him over onto his back.  He was left gasping.



Golem shifted his head, saw his own chest as a mess of blood and grit from the road, a ruin of shredded armor.  The damage extended down his legs to the tops of his boots.



Further down, Jack rode Hookwolf like Hannibal astride his elephant, a small contingent of his `army' behind him.



``What was it I said, back then?  Crotch\ldots''



Jack lowered the blade, pointing.  He stabbed it forward a fraction, and Theo felt the impact on his armor, between his groin and his thigh.



``To\ldots''



Jack moved the blade.  It dragged along Golem's intact armor, and he could feel metal parting, the armor shifting, pulling against his ravaged chest.



Like a dream, something surreal.



He thrust his hands into the panels at his sides.



Hands emerged from his ruined armor, no larger than his own.  Each hand grasped the wrist of the other, pulled to draw each other closer together, to draw the ruined armor together.  Jack's blade moved faster, before Theo could shore up the rest, raking across his ribcage, shoulder and the edge of his chin.  He could feel the blade rasp through bone.



Jack didn't lower the sword after striking.  He left it there, his arm extended, the point aimed at the horizon.



It was a cue, an \emph{order}.  The Nine began advancing, a crowd of them.



``D--'' Golem started to speak, but his face was too ruined.  Couldn't see out of one eye, and that cut to his chin made even moving his jaw too painful.



``\emph{Red}.  \emph{Eleven.}``



He didn't even have to think about it.



He created two more hands.  Large hands.



It was a gamble, but any maneuver would be in a situation like this.  Two hands, each on opposite sides of the street.



Just as Theo had created hands to jab at Jack's knees or to strike at Crimson's weak points, he created them to strike at a different sort of weak point.  Shaped into fists, the hands slowly, inexorably extended into the corners of buildings.



When the hands stopped making headway, he opened them, felt how slow they were to move, as if he were flexing his hands inside thick clay.



Nevertheless, he closed the hands on major supports, and pulled, withdrawing them back into the ground.



Had Bohu made the buildings sturdier in the course of attacking the city?



Theo used the last vestige of strength to \emph{wrench} with one hand, to \emph{twist}, in an attempt to get that one vital support to come down.



The building remained standing.  Too thick, too solid.



But the building on the other side of the street, the one he hadn't touched, it shifted, then slowly toppled into the middle of the street, leaning slightly away from Golem in the process.



Which helped less than he might have hoped.



He reached down once more, feeling the pull against cuts on his chest as he moved his arm, and a large hand emerged from the ground, helping him to his feet.  He used it for support as he got his feet under him.



He felt as lightweight as a cloud, but that was deceptive.  His armor was heavy, and his strength was dribbling out of him in a hundred thin streams.  He moved in a deliberate way as he planted one foot in front of the other.



He could patch up his armor or he could knock down more buildings.



``\emph{D- muh},'' he mumbled.



``\emph{Red.  Help's on the way.  Ten questions left.  Do your best.''}



Golem began tearing down the next set of buildings.  Too many in that group of Nine would survive or avoid the impacts, but it was something.



Ten questions, and Jack was still okay.  Jack was too quick, too fast.



It reminded Golem of sparring against Taylor.



He hadn't won those fights either.



Hadn't won any, up until the point where the deadline for the end of the world was imminent.  He suspected that was a mercy, a small encouragement.  An intentional loss.



The buildings crashed down behind him.  He couldn't run, but he could manage a limping jog.  He began to patch up his armor.



There was a sound of a blade leaving its sheath, somewhere behind him.



He turned, and saw a Mannequin approaching, rounding the corner at the end of the alley.  Blades extended from the tinker's forearms.  The expressionless face still managed to \emph{stare}.  If anything, it was more expressive than half of the people Golem interacted with, by virtue of body language alone.  It moved with a kind of anticipation, let itself shift and flop this way and that, almost in a taunting way.  With \emph{swagger}.



Golem backed away, found himself at a corner, and turned to enter the adjoining alley.



A wall of criss-crossing blades barred his way.



Bohu's work.



It made him think of his father, a man he had to go to great effort to see as his \emph{dad}.



Golem reached into the wall, saw the Mannequin move, dodging the outstretched hand.



He extended another hand, and it reached out from the first's palm, catching the Mannequin around the throat.



\emph{Entomb}, he thought, almost hearing Weaver's voice uttering the word.



He created more hands, binding, holding, getting as much of a grip as he could manage against a foe that was as smooth as chrome, hard as crystal.



His target struggled and squirmed, very nearly slipping free as he let his neck disconnect, cut the chain that attached torso and head.  Golem caught one leg around the ankle.



Mannequin disconnected that too, leaped-



And was cut short by a hand emerging above him, knocked back down atop the lump of frozen hands of concrete and brick.  Theo gripped Mannequin's arms and legs, then extended one arm and punched one hand into the neck-socket the head had fit into.



Others were approaching at the end of the alley.  A Crimson, swollen with blood.



The man barreled through the alley, his path of destruction not reaching the hands that held Mannequin a matter of feet over his head.  A Murder Rat followed just behind him, pointing with one foot-long blade.



Signaling others.



Theo used hands of stone to break and bend the lattice of blades, then created more to fashion a set of stairs, footholds to walk up as he made his way to the roof.



Footholds too fragile for Crimson to use, with his excessive weight and massive feet.



The man started to climb, and Golem interfered.



The Murder Rat was a bit of a problem, though.  So were the ones that were due to follow.



Using hands and feet both, he made his way up a hand-made staircase without rails, approaching the rooftop.  He concentrated, collapsing more buildings.



Ran his fingers along the panels, and felt the steel in Hookwolf's body, as the creature moved Jack out of the way of danger.  Siberian would be close.



Golem used his power to find the concrete, finding the area closest to where Hookwolf had been, and then began bringing down more buildings.



Slow, too ineffectual for a face to face fight, but it was a good way to apply \emph{pressure}.  Keep Jack on his heels, wondering if Golem was close.



Heartless, ruthless, \emph{reckless}, even.  There was no telling which heroes were near.



But the Golem of myth, the creature of clay fashioned by the Rabbi Bezalel, was heartless as well.  There was only the will, the order, the \emph{message}, inscribed on its forehead.



Fitting, in a way.



He'd regretted choosing the name, not long after Weaver's video of New Delhi had reached the public, setting the identity and name in stone.  Regretted it because it was petty, because it was ill-fitting, and above all, he came to regret it because of the heartless nature of the creature he'd named himself after.



Now, he clung to it.  The message, the objective.



He reached the top of the staircase he'd made and came face to face with Chuckles.



The clown was fat, tall, and generally pear-shaped.  It was dirty, grungy, almost \emph{fetid}, smelling of sweat and blood and worse things.



\emph{No wonder.  He can't even clean himself, with arms like those}.



The Chuckles had arms that zig-zagged, consisting of more elbow than arm.  They trailed behind him like ribbons, and the hands at the end were large and blunt-fingered.



``Ha,'' Chuckles said.



The clown drew one arm close, folding the elbows, then lashed out with a surprising speed, extending the elbows all at once.



Golem let himself fall face-down on the rooftop before the fist could connect, unsure if he'd even be able to rise.



The clown laughed, a discordant sound, as if there were a different voice for each syllable of the utterance.



\emph{Super speed in the head and legs, super strength in the chest and arms.  He had to deal with perceiving the world too fast, unable to communicate.  Only managed to teach himself to make a sound like laughter.  Kind of.}



Went crazy.  Like Purity's going to\emph{.}



Already, the clown was preparing to strike again, planting his feet, rearing back, and condensing one of his accordion-arms by folding all of the elbows.



Theo reached into the ground, creating a large hand from beneath Chuckles.  He closed the fingertips on a single point.



Chuckles crumpled, but Theo's grip between his legs was strong enough to hold him upright.  Hanging limp, in too much pain to move, Chuckles giggled.  A strained sound.



A scrape marked an approach at the other edge of the roof.  Golem raised his head and saw a Murder Rat approaching, trailing her claw-tips on the ground.



``\emph{Cuh},'' he managed a single syllable.



``\emph{Red}.''



Attack?



He lashed out, and she dodged.



He struck out, this time with two interconnected hands, and she slipped out of reach.  Too fast, too flexible.



She closed the distance as he rolled onto his back.  From various collapses and falls, he'd had dirt caked into the wounds.  It might lead to blood poisoning, might lead to infection, but it was helping to staunch the blood.



Fat lot of good it would do him now.



He reached for a panel, but the blades of her claws punched into the ground around his wrist, pinning them.  He moved his other hand, and she did the same.



Couldn't move his wrists.  His feet-



He didn't have the abdominal strength to raise them.



Her mouth, conical, shaped by surgery into the vague shape of a rat's snout, riddled with canines, lowered towards his face.



\emph{Her eyes are so human}.  \emph{I wouldn't have thought}.



He closed his eyes.



Golem seized up in pain as he felt something press up against the left side of his face, twisting every wound that had already been present.  A tongue draped against his chin, and he could feel her hot breath.



Hot blood flowed around his neck.



Enough that he could put the pieces together.  Know that it was too much for any one person to survive, no matter how immediate the medical assistance.



``Golem.''



He opened his eyes to see Weaver perched between Murder Rat's shoulderblades, her flight pack glowing.



Murder Rat had collapsed, her face against his.  Her eyes were rolling up into their sockets.



The blood that was flowing wasn't his.



``Shit, I can't believe you made it,'' she said.



``Nuh,'' he responded.



\emph{Not so sure}.



Weaver hopped down, then kicked Murder Rat off.



He wanted to hide, to crawl away.  They'd put so much time into it, but in the moment, eye to eye with his enemy, he hadn't been able to manage it.



He'd failed to kill Jack.



``Can you fight?  Do you need me to get you help?''



He shook his head, not sure which question he was answering.



But he was able to raise his hand, then lower it into the rooftop.  He pushed himself to a standing position with his power.



Bitch was present, along with Tecton, Parian and Foil.



He felt the painted steel panel, sensed Hookwolf.  So little of Hookwolf was usable, his power needing sufficiently \emph{thick }material to use, but he could track the man.



His least favorite of his dad's old lieutenants.  Kayden had been kind, if not quite a mother.  Krieg had been respectful.  Hookwolf had treated him as the fat, scared little boy he'd been.



He pointed in the direction that Hookwolf was.



``Jack?'' Weaver asked.



Golem nodded.



``You stay.  I'll call for help, and we can go after Jack.''



``Nuh,'' he managed.  He set a hand on her wrist.



``Okay,'' she said.



``Golem,'' Tecton said.  ``I know I'm not your team leader anymore, but-``



He realized how hunched over he was.  With excruciating effort, he managed to pull himself to an upright posture, meeting Tecton's eyes.



``You're too hurt.  You're dead weight.''



``\emph{I could use my power},'' Dinah said.



``Nuh,'' he said.



``We let him come,'' Weaver said.  ``Parian?''



``On it.''  Parian hopped down from the dog's back.  Spools of thread unfurled, each tipped with a needle.



\sectionbreak



The dog landed on a rooftop.  The pain was bad enough he considered throwing up, or throwing himself off.  Either would probably tear stitches.



They approached one spot at the edge of the roof.  Golem accepted help in dismounting, then eased himself to the ground.  The others hunkered down to get a view of the scene on the street below.



``\emph{Nostalgic},'' Weaver said, her voice barely audible.  Rachel grunted.



Jack was atop Hookwolf, giving orders to his minions.  The Siberian was on the ground.



Foil lowered her crossbow, aiming.



Weaver placed a hand on top of the weapon.  When Foil looked her way, Weaver shook her head.



``It's not him,'' Weaver whispered.



A monster that looked to be one of Nilbog's creations, outfitted with one of Bonesaw's control frames crawled along the edge of a rooftop.  It perked up and looked at them, tensed.



Foil shot it before it could open its mouth.  It died without a sound.



Chevalier approached.  Nearly blind, he crouched in the center of the roof.



Hoyden and Revel were conspicuously absent.



``He\ldots'' Golem started to speak, winced.



Heads turned his way.



``He's\ldots like Weaver.  Some\ldots other power.''



``Another power?''  Tecton asked.  ``People have speculated, but--''



``But\ldots few survive meeting him.  Minor.  He\ldots probably doesn't know.  But\ldots reaction too fast.  Too efficient.''



They fell silent.



``A thinker power?'' Tecton asked.



Golem considered, then nodded slowly.



``I believe it,'' Weaver said.  ``Like me?''



``Senses things\ldots that kind of reaction time.''



``Tattletale?'' Weaver asked.



At first he thought she meant \emph{like} Tattletale.



No.  It was a question.



``\emph{Yes,}'' Tattletale said.  ``Can't say much more than that.  Sorry.  Drawing blanks.''



``Trump card,'' Golem said.  ``Dinah.''



Heads turned.



``She's talking to you,'' Weaver said.  ``We can give ourselves optimal odds.''



``\emph{Yes},'' Dinah said, but from the reactions, she spoke only to Golem.  ``\emph{Seven questions, Theo.}''



Seven questions.  Seven chances to make this count.



Red or blue wouldn't cut it.



``We called for reinforcements.  Chance of assistance from outside?'' he asked.



``\emph{I can answer that for you,}'' Tattletale said.  ``\emph{You've got capes converging on your location.''}



``\emph{I'm not asking},'' Dinah said, ``\emph{You've still got seven questions.  But the more time that passes, the worse chances are getting.  I can see a lot of dead ends coming up.  You need to act.}''



``If we attack Jack right now, what's the chance of the world ending?''



``\emph{Ninety-seven percent chance, but the alternative is worse, and it's getting worse every second!}''



He barely had time to register the thought.



This was it.  The moment.



``Go,'' he said.



The defending capes moved in.  Foil slid down, her cleats digging into the surface of the building to afford her some drag, then leaped off to stab a Crimson through the skull.



Tecton \emph{jumped.  }His intact piledriver-gauntlet punched the ground, breaking his fall by making the surface almost fluid.



He struck the ground again, and the shockwave destabilized every one of the Nine in the enclosed area.



Foil threw darts, killing two more.



Parian's stuffed creation landed atop Hookwolf's head, and the two dogs used the opportunity to leap down.



Jack's defending group of minions was thin at best.  The one atop Hookwolf moved to stand-



And was promptly shredded as Hookwolf stirred into action.  He shook, and the illusion was turned into a cloud of smoke, billowing out towards Foil, Tecton and the dogs.  The two young capes staggered back, covering their noses and mouths.



``Where's Jack?'' Golem asked.  His entire body ached, and a heavy feeling, like a bruise multiplied in intensity a thousand times over, had settled in his abdomen, making it hard to breathe.  ``Left or right?''



``\emph{Left}.''



He turned, moving towards the edge of the rooftop.  A Hatchet Face, Breed, Cherish and King made their way towards the entrance of the alley.  Golem created hands to block their path.



The Hatchet Face raised his axe, then chopped at the hand.  It cut a gouge into it.



Golem created a large hand at the roof's edge, then pushed it off, dropping it straight onto the two villains.



The concrete fist shattered into pieces.  Impossible amounts of dust billowed out from the \emph{hit.}



\emph{Did I get him?}



No.  The Hatchet Face marched on, pushing at the hand and shoving it down.



On the other end of the alley, Hookwolf's body of whirling, scraping blades altered, becoming more shapeless.  No legs, no arms.  Just a blob.



A blob capable of moving with surprising speed.  It leaped up onto a building face, then dropped down towards Foil.



Golem changed tactics, using his power to block the blob.  He failed, serving only to change its course.  Foil was quick enough to leap to one side.



The second the blob landed, the sheer surface area meant the countless blades that all moved in the same direction were able to get a grip, like a monster truck tire spinning freely.



It meant that Hookwolf was able to reorient himself, veering straight for Foil.



Parian's creation threw itself at him, sandwiching him between it and the wall.  Blades and hooks scraped against fabric, but failed to deflate the creation.  Momentarily, he was trapped.



Golem raised large hands to cup the blob, holding it in place.



Up until the moment Hookwolf deformed himself, flowing through the gap between the hands like a fluid.  He perched himself on twenty or thirty stilt-like legs, raising himself above the ground, surveying the area.



A second later he lunged, and one of Rachel's dogs intercepted him.  Blades shredded one muscular, bone-encrusted leg.



Chevalier, standing at the roof's edge, took careful aim and then shot Hookwolf.



Hookwolf's individual components scattered everywhere as a hole was blown into the shifting mass of metal blades.



But he reformed himself again, a wolf-headed serpent, too narrow a target to shoot.



The gang of lesser Nine members approached the periphery of the fight, but they didn't join it.  They watched as Hookwolf fought.



``\emph{Where's Jack}?''  Golem asked again.



``Five questions left.  To your right.''



He glanced left, then right.  Tried to imagine the paths Jack might have traveled in the span of time Dinah had suggested.



Weaver was drawing her swarm together, and she attacked the least likely target.



Her bugs flowed into Hookwolf's shifting mass of blades.  Countless bugs no doubt died.



\emph{Silk thread?}  Golem thought.



Except Hookwolf wasn't even slowing down.



Weaver drew out a line of bugs across the alley.  Foil rolled, raised her crossbow-



Hookwolf slashed out, extending a long, wavy piece of metal to cut at the crossbow.  Foil pulled it out of reach, but her shot went wide, sailing off into the distance.



She drew her rapier from its sheath, throwing it in the same motion.



It penetrated Hookwolf, sailed past him to impale the side of one of the tombstone like buildings.



Hookwolf wavered, then collapsed into a heap that looked like it would make for an exceedingly dangerous game of pick-up-sticks.



\emph{Where's Jack?}



Left, then right?  He'd ask again, but he couldn't help but think that he'd get an equally perplexing answer.



He hadn't seen Jack move.  \emph{Weaver} hadn't seen Jack move.



There was a crash as an Azazel landed at one mouth of the alley.  Heroes deployed.  a battered Cuff and Grace.  Clockblocker, Kid Win and Vista\ldots



``\emph{Defend the perimeter!}'' Chevalier ordered.  He lowered his cannonblade, pointing it at the newly-arrived Nine.  They tensed, but the King looked over his shoulder at the Cherish, and when he looked up again, he was \emph{smiling}.



``Hold off!'' Golem said.



Chevalier stopped.



Weaver was amassing her bugs, poising them for an attack on this squad of reinforcements.  The bugs stopped as well.



No.



Something was wrong.



``\emph{Shit on me.  I can see through Chevalier's helmet-mounted camera.  It's a trap!''}



He'd been right.



He reached down, using his power.  The mouth of the alley was narrow.  Easy enough to close off, trapping the villains within.



Two hands, positioned to divide this group of Nine from one another.



They reacted, backing away as giant hands rose like tall, narrow walls, separating them from one another.



Two remained untouched.  The King and Hatchet Face.



\emph{Or}, Golem thought, \emph{Jack and Siberian}.



Weaver was already attacking, and it was a form of attack that suggested she knew \emph{exactly} who she was up against.  Bugs flowed past them, stringing thread, binding.  The two in the back were the targets.  Nothing she could do against Siberian or Jack.



Golem struck out, two hands reaching out from the walls on either side.



He felt a moment's hesitation.



``Dinah.  Attack?''



``\emph{Attack}.  Chances are getting better.  Ninety-two percent.''



Monsters, but\ldots



The training had offered \emph{something}, at least.  Or maybe the pain he was feeling with every breath served as a motivator.  He managed to find the aggression inside himself, to strike out at someone who wasn't even aware of him.



The illusions collectively shattered as he squashed the head of the `Cherish' against the wall.  Nyx.



Which revealed the other three.



Jack.  No surprise.  Hidden inside King.



Siberian.  To be expected.



And Gray Boy, squashed against the wall.



His heart dropped.



He drew in a deep breath, feeling every sutured wound straining, very nearly coughed and lost the air he needed.



``Gray Boy!'' he shouted.



Just the act of shouting made him double over in pain.



``Run!'' Weaver called out.



Tecton slammed his piledriver into the wall.  The cloud of debris offered a small amount of cover.  Too small.  It wouldn't be enough.  He ran, and Bitch whistled, the dogs stampeding past her.



The corpse flickered, and Gray Boy reappeared, sitting atop the forearm of the hand that had squashed him.  He hopped down.



His time loop power protected him.  Any time he was hurt, any time he was debilitated, his power would kick in, taking him back as far as he needed, allowing him to maintain his position if he wanted.  He'd remain conscious, retain any recollection, and with his \emph{offensive} power, he could shut down any threat.



It was that same power that kept him from aging.  Aging was a danger, \emph{change} was a problem, so he continually retained his appearance from the very moment he'd triggered, reverting back several times an hour, or any time he even got dirty.



A multifaceted, instinctive defense.  An offense that could trap Scion.



Parian's creation blocked his view of Foil and Tecton.  He froze it, looped it.



Jack, for his part, drew his sword.  He cut, and the weapon sliced through the cloth.



``That's spider silk,'' Parian said.



Three questions left.  Three moves.  The last few had bought them time, had broken the illusion.  They hadn't been caught off guard, at least.



Foil threw darts.  Gray Boy froze them in mid-air.



Weaver's bugs dissipated through the alleyway, blocking Gray Boy's sight.  Cover, for her allies.



``Doesn't matter,'' Gray Boy said, his voice high.  ``Don't really need to see.  Just have to guess.  Stop running!''



He used his power, and the area at the far end of the alley was frozen.  A ten foot high wall of looped air.  Tecton slammed into it, struck the air as if it were a solid wall.



He punched the wall, and it shook.  Gray Boy proceeded to freeze the walls on either side.



A dead end.



``Shooting in the dark,'' Gray Boy said.  ``Let's see.  There!''



One section of bugs were caught, trapped in a loop.



``A miss.  Phooey.  There!''



Another section of bugs frozen.



And Foil shrieked.



Shrieked again.



Shrieked again.



A loop.



Parian's own scream joined Foil's, but there was no loop there.



``Gotcha,'' Gray Boy said.



Weaver hung her head.



``We're going to walk out of here,'' Jack said.  ``In\ldots about five minutes.  We'll freeze everyone we see.  Tell them to run if you want.  It won't matter.''



Foil's screams continued.  Each the same length, with variations on the tail end, as she managed to reassert control over the bodily impulse that was being performed anew each time.



Jack and Siberian advanced, passing Gray Boy as they closed the distance on Tecton.



``How much more damage can we do?  Is it a question of doing as much damage to as many people as possible?  Can we get a second trigger event out of one of you?  Bring about the end of the world?''



Jack seemed so pleased with himself.



\emph{Jack has a thinker ability.  }



\emph{What?  Not precognition.}



``Or is it about doing something \emph{significant?  }Does killing Scion count?''



The heroes outside the perimeter were aware Gray Boy was inside.  Had to be, by Foil's voice.  They were caught between watching for outside threats, of which there were bound to be few, and guarding against an approach from within.



\emph{What does Jack do?}



He grasped for a thought and failed.



No.  He needed to think about it from a different angle.



What does \emph{Weaver} do?



``Dinah.''



``\emph{Three questions left.}''



``What's the chance?  For what I'm thinking right now?''



``\emph{Allowing for the fuzz I'm getting from Scion's presence above you?  Seventy.}''



Seventy.



``\emph{The numbers are better,}'' she said.  ``You're on the right path.''



``I know,'' he said.



Jack had raised his sword  to Tecton's throat.  The Siberian stood behind him, one hand on his shoulder.  Gray Boy looked up and Golem leaned out of sight.



``Weaver, you have anything up your sleeve?''



``Yes and no.  A way to stop Siberian, maybe.  \emph{Or }Gray Boy, \emph{maybe}.  But\ldots I need an opening to do either.  A distraction.  And whichever one we \emph{don't} stop is going to \emph{destroy} us.''



``Okay,'' Golem said.  ``I'll get you that distraction.''



``Was going to use my bugs, get Clockblocker.  With him, \emph{maybe }we can take out both at once.''



``Don't,'' Golem replied, tensing up despite himself.  He'd nearly raised his voice to the point that Jack could hear.  Foil's continued screaming drowned him out.



``I\ldots won't.  What are you thinking?''



``That there's an answer.  A stupid, silly answer.''



He stood, resisting the urge to groan, and he approached the end of the rooftop closest to the heroes who were defending the areas outside of the alleyway.



He gestured, signaling to one.  When they didn't move, bewildered, he created a hand, pushing them.



Others, he stopped.  A shake of his head.  Clockblocker was out.  So was Imp.  Grue, Vista, Kid Win, Cuff and Grace wouldn't do.



Only this person would serve.



``Two more questions?''



``Yeah.''



``Left or right?''



``\emph{Right.}''



\emph{The long way around}.  Not the way he would have expected.



``Now, or wait?''



No response.



He gestured, and he created hands pointing the way.



``\emph{Now},'' she said.



He shut his eyes.  This was it.  Last question asked.



``Be ready,'' he said.



This would be the moment everything fell into place.



The man made his way down to the end of the alley, and Golem created more hands;  six hands in a matter of seconds, sticking out of the wall.  Each pointing in the direction they needed.  He created a platform and started raising it.  Raising their potential savior up towards the top of the wall of looped time.



``You're- he's walking into a trap,'' Weaver said.  ``They'll see him.  They're looking right at him.''



Something was wrong.  Something missing.



``Attack.  Sound the attack.  Distractions!''  The words were wheezes.



Weaver signaled, her bugs drawing words.



Chevalier shot his cannonblade into the far end of the alley, furthest from the villains.



Golem created a hand.



Just what they needed.



The man leaped down from the top of the wall.  His light armored suit absorbed his fall, made it quiet.



The D.T. uniform.



He sprayed containment foam at both Jack and Siberian.



Nothing.  It wouldn't achieve a thing.



But Tecton took the moment of Jack's blindness to duck, to strike the ground.



The Siberian wasn't immune to gravity.  She fell, and just for a moment, she broke contact with Jack.



Tecton slammed his fist into Jack's stomach.



The D.T. officer had turned the containment foam onto Gray Boy.



Except Gray Boy reappeared, out of the way of the stream.



The containment foam froze in mid-air.



\emph{No}.



The Siberian leaped out of the fissure, then paced towards Jack.



Her hand stopped an inch away from him.  She lowered it.



Jack had turned gray.  Trapped, looped.



``Pathetic,'' Gray Boy said.  ``Stupid, useless.  I thought you'd do something \emph{interesting}, but you made yourself prey, instead of the predator.  If you're going to be prey, I want you to be \emph{my} prey.''



It dawned on Golem. \emph{ Gray Boy froze him}.



Foil's screams continued, and were soon joined by Jack's, as Gray Boy started using his knife, reaching within the field.



Up until the moment Foil, still screaming, using her augmented sense of timing to measure the length of each scream, stepped around the monochrome field he'd cast just in front of her.  She threw a handful of darts through the Siberian and Gray Boy's head as his back was turned.



The Siberian flickered out of existence as Gray Boy collapsed.



Neither reappeared, healthy or otherwise.



``Get back from Jack!''  Weaver called out.  ``Quarantine him!''



Tecton used his piledriver, erecting a shelf of earth.  Golem stepped back, then did the same, folding large hands around Jack.  Jack's voice was mellow, inaudible, with a funny cadence.



The D.T. officer, for his part, tore the containment foam hose free.  He got gunk on himself, but he managed to direct the resulting stream at the gaps.  Sealing Jack, burying him.



They stood in silence, waiting for the other shoe to drop.



``We got him,'' Weaver said.  She raised a hand to her ear.  ``We got Jack.  He's \emph{down}.  Everyone report in.''



``\emph{Houston is safe},'' Defiant reported.  ``\emph{Battered, but safe.}''



``What are the numbers?'' Golem asked.  ``Dinah, if you give me \emph{one} more answer today\ldots''



No response.



``\emph{Reporting from New York.  We told Bonesaw Jack was down, and she just surrendered}.  \emph{No idea what to do.}''



Chevalier answered, giving instructions for containment.  Bonesaw was loaded with viral charges and worse.  Quarantine was best.  Nilbog could be taken to a secure facility.



``That's\ldots are we safe?''  Golem asked.



``Unless the catalyst event just happened,'' Weaver replied.  ``Get sorted, get organized.  First aid, asap.  We need to check all info, then we quarantine ourselves for the time being.  Stay calm, stay focused, be alert.''



There were nods all around.



They made their way to the ground.  Waiting as the others joined them.



Weaver looked at Bitch.  ``Guess we can hang out for a bit, while we wait to see if there's any lingering effects or traps.''



``Hanging out sounds good.''



She looked at Golem.  ``Yeah?''



He shook his head.  ``I don't--''



``I don't either,'' she said.  What they \emph{didn't }was unclear, but the message still served.  ``You beat Jack in the end.''



``I wish I was so sure,'' he said.



``So do I.''



A long pause reigned as Tecton and Foil caught up with them.  Parian wrapped her arms around Foil, openly sobbing.



``Anything?  Any clue what might have happened?''  Weaver asked.



``No,'' Bitch said.



``No,'' Golem answered.



``Jack said something,'' Tecton said.  ``I don't\ldots I don't think I should say it.''



Just like that, the peace was gone.



``Was it--'' Golem started.  ``No.  Stay quiet.''



Weaver hung her head for a moment.



``I don't think it was the catalyst,'' Tecton said.



``Pick someone you trust,'' Weaver said.  ``Someone you know to be sane and safe and non-dangerous.  Then whisper it.  They'll give a second verdict.''



Tecton's eyes fell on Golem.



Golem nodded.



Tecton leaned close.  ``\emph{Doesn't make any sense.  Nonsensical.  He said-}''





