





The entity swims through the void and it \emph{remembers}.  Everything is stored, dating back to the very beginning.



In the beginning, a species chokes their gray planet.  Here and there, landmasses appear, created by inhabitants to trap or uncover the scarce food that exists, but the landscape is largely liquid, water thick with silt and other particles.  The creatures worm in and around one another, and the planet has as much space taken up by the creatures as there is space left for other things.



Each has evolved the same capacity to shift between layers, to explore the alternate versions of this same world, and each of these other worlds are choked by more of the same creatures.  Still, they continue to reproduce, and in their spread, they have eradicated virtually every source of food from every world they can access.  The species is so numerous that it is nearly impossible to find space to surface at the uppermost areas of the water, where they might absorb starlight and radiation.  What little energy they do manage to acquire in the process is lost in struggles to stay at the top and the continued efforts to avoid being pushed and pulled down by the coils of their neighbors.



\emph{Tangle.}



The ancestor is aware of this, fully cognizant that the fight over resources will soon reach a climax, and there will be a war where every creature fights for itself.  These wars are not graceful or sensible.  The strongest can be torn apart as easily as the weakest.  Once it starts, it will only end when a meager few remain.



Then, as they retreat to individual worlds to mend and restore themselves, the prey will multiply, and there will be a span of feasting for those lucky enough to survive.



With that, the process will begin anew.  The same things will occur.  This has happened no less than one hundred and seventy times, with little variation.  Each time it occurs, realities are left dead, the grace period before resources run out once again is shorter.  That the number of worlds exceed the number of particles that might exist in one world's universe is inconsequential; the creatures multiply exponentially.



They are running out of time.



The ancestor knows this, and it isn't satisfied.  It knows its kin aren't satisfied either.  They are quiet, because there is nothing to say.  They are trapped by their nature, by the need to subsist.  They are rendered feral, made to be sly and petty and cruel by circumstance.  They are made base, lowly.



With all of this in mind, the ancestor broadcasts a message.  Each member of the species is made up of cells, of shards, and a typical broadcast is a simple concept, a single message nuanced by a million individual influences brought to bear by the shards that made up the speaker.



\emph{Proposal.}



The message is voiced with violence, across innumerable wavelengths and means, through heat and motion and electromagnetics and light.  Each shard cluster retains different abilities, minor tools for self-defense and offense, for finding prey and helping the ancestor make its way in the cold gray mud.  In communicating, it turns the vast majority of these resources outward, to transmit the signal, and each form of communication has different ideas, different subtleties.  In this, a greater, complex communication is achieved.



The act of speaking nearly kills it, it is so starved for energy.



It continues, and because this message is so different from the screams and cries over food and territory and everything else, the others listen.  They expend their own energy to transmit it further.  The idea spreads across every possible world like a ripple.



A species needs to continue evolving.  It needs conflict and variation.



Failure to meet these objectives leads to self-destruction.



By the time the ancestor is finished communicating, it is depleted, unable to even move as it is shoved by the bodies of others that swim past.



Then, in bits and pieces, it is devoured.



Devoured not for energy, but for material.



The shards are absorbed, made a part of the eater, and the ones who eat swell in size.  Unsustainable sizes, but they grow nevertheless.



All across the possible worlds, the creatures turn on one another.  It is a war, but it takes a different shape, a different form.  This time they are not eating for energy, but to stay afloat and stay large enough that they are not subsumed by a greater whole.



The gray planet makes several revolutions around its star before things reach a climax.  Many of the creatures are so large they cannot subsist in one world alone.  They weave into one world and worm out into another.  Every flank is vulnerable to another of its kind lunging out into a world and attacking, consuming whole chunks at a time.  Heat, cold, electricity and mental manipulations are leveraged in these struggles, slowing their targets down enough for them to wrap themselves around, shear off a section to take into themselves.



More revolutions, and only a handful remain.  Energy is scarce, even with the individual bodies taking up whole oceans of the thin gray mud, absorbing all of the light and radiation they can.  Countless worlds have grown dim, absorbed of all possible life and nutrients in the course of struggles and fighting.



The smallest ones recognize the fact that they don't have energy, that it would cost them all too much if they continued fighting this uphill battle.  They submit, and are consumed.



Two remain.



They spend time reorganizing themselves, shifting the sheer masses of shards they have acquired into forms useful for another task.



Once they are reformed, they leech all of the heat and energy from countless worlds and concentrate it in a single reality.  The energy boils the oceans of silt-choked waters, disintegrates the landmasses.



Their bodies form into a large, complex shape, with only small fragments in this one world.  The extensions of those same fragments extend into other realms, in concentrated, specific shapes, made for a purpose: to survive the next step.



The energy is released, and the planet shatters.



The shattering is so extreme that it extends into other worlds, through the same channels that the fragments used to extend into other realities.  Every single one of the remaining habitable worlds is destroyed in the ensuing blast.



And the fragments radiate outwards, shedding and dropping their protective shells as they sail into the black, empty void.



\emph{Gestation.}



Still flying through the void, the entity forms the word in the midst of its recollections.



They are children.  Offspring.  They travel the void, hoping to encounter another habitable world.



This is the beginning.



Countless perished, no doubt, in contact with lifeless moons, expending the last of their energy to search the possible iterations of that moon for life.  More die within moments of the detonation, their outer casing too damaged, vital processes separated from one another



But others made contact with other worlds.



A world with life rooted in landmasses, weathering brutal storms of caustic acid.  The one who arrives on that world struggles to find a means of survival.



It finds refuge in one of the dying plant structures, provides ambient heat to nourish it, so that the openings might close up and the shelter be made more secure.



The planet revolves around its star many times.



Many, many times.



The one that occupies the structure has bred, now, fragmented into clusters of shards that could occupy others.



Some shards have different focuses.  This is the experiment, the test.



Of these plants, some thrive.  Others die.



The creature tests different capacities, different clusters of shards.  It watches, observes and records events into memory.



It borrows of the conflict and stress of this new, alien species.  It borrows of the evolution, of the learning, of the crisis.  In some ways, it is a symbiote.  In others\ldots



\emph{Parasite.}



The fragments continue to divide, feasting on abundant resources, on light and radiation and the alien food sources it has started to learn how to consume.  It spreads quickly now, across every possible variation of this world that sustains life.



It encounters another.  A later arrival to the same planet, a member of its own species, another that is multiplying and consuming and growing.  This new arrival chose a different means of survival, but it too chose a kind of parasitism.



They exchange shards where they meet.  In these shards are codified memories, as well as the most effective techniques they have observed.



The planetoid is small, the range of options limited.  A message is broadcast.  Mutual agreement.  They will move on.



\emph{Migration.}



The process is similar.  Drawing themselves together.  There is cooperation, this time, as each shard returns to the source.  The hosts die in droves, and are absorbed for energy.



They gather into the same vast forms that span multiple realities, and they leech energy from other worlds to fuel their exit from a single one.  It takes time.



But something else occurs.  A broadcast from the other, followed by an attack.



A carefully measured attack.  The two creatures ruin one another with friction and pressure, burning hot, and shards are destroyed.  Many are partially destroyed.



The other creature joins shards together into combinations, discards and destroys.  Repeats the process.



New shards are created.  Different functions.  Forced mutation.



The end results parallel the studies the creatures have made of the plant life on this planet with its acid rain.



More blatant than intended in the beginning, but nothing lost.  New strengths, regarding growth and durability.



They concentrate the energy as they form themselves into an encasement around the small planetoid.



\emph{Shell.}



The detonation of the small planet scatters the individual clusters of shards, and this time, they are better inured to the harsher elements of space.



So the cycle continues.



The next world encountered has sentient life, civilization.  A complicated, rich world.



It is a symbiosis, this time, more than parasitism.  The two species learn from one another.  The shards code the `technology' of this new species into their memories.  They learn of warping space and gravity.



Until the species turns against them.  Those lucky enough to bind with the entity's offspring war against those who do not.  Some seek to rule.



\emph{Monarchs.  }The entity forms the thought, defining the memory.



The cycle is cut short by a forced exit, as the shards are rooted out and destroyed by the natives of this civilized world.  They meet, they bind and again they share ideas.  Richer perceptions, complex technologies and more are fashioned in the unity of three larger creatures.  It is through differences in the greater entities that a richness is created, new derivations, new connections that none would be capable of on their own.



The planet is expended, the offspring are cast off in every direction once again.



This time, they are capable of moving, of controlling their course.  Gravity, warping space.



The entity recalls all of this as it swims through the void and makes its way to the next target.  It can reach back into the depths of its memory to recall all of what came before.



Each time the cycle started anew, lessons had been learned, methods refined.  Each time, the spawn that are spewed out from the destroyed planet are more robust, larger, hosting innumerable memories.  Where memories fall in parallel, they are shared out, offered to others.



After more than three thousand cycles, there are safeguards, there are protections.  The arsenal of abilities, powers and protections the creature possesses have been built up.  The entity remembers past failures and has adapted so they will not happen again.



The entities travel with partners now, moving in spirals while maintaining a measured distance from one another.  Each is slightly different from the other, taking on a different role.  Attacker and defender, warrior and thinker, builder and destroyer.



This divide is so they are able to take a different stance, shape their shards in subtle ways and clarify the results when their shards are compared and joined once again – some shall be kept, others discarded.  Some will turn up interesting possibilities that can be explored when new shards are invented at the cycle's end.



These individual focuses drive the pair, shape their tasks as they approach their destination.



The entity reaches out with clairvoyance, with precognition, and it views its destination.  It communicates, covering vast expanses of space, transmitting signals across channels formed of the very foundation of this universe.  These signals are broadcast only across specific realities, so that no aftereffects or lingering transmissions will contact a version of that world that hosts no life at all.



\emph{Destination.}



\emph{Agreement.}



\emph{Trajectory.}



\emph{Agreement.}



Each signal is nuanced, shaped with subtle details and clues by the trillions upon trillions upon trillions of individual shards that make up the entity.  Through these nuances, it conveys more information than an entire planet of sentient beings might in a hundred revolutions.



They have settled on a target.  Old lessons are remembered.  It is a planet of sentient lifeforms, more primitive than some the entities have run into, more advanced than others.  Social creatures, forming communities.  These societies teeter on fine balances, but they persevere nonetheless.  A world rife with conflicts, big and small.



\emph{Agitation.}



The new hosts are to be bipeds, with a binary reproduction.  Not uncommon, and rich with potential.  Such a division and natural competition for reproduction fosters a natural evolution and development.  The entities will focus on them over any of the sub-species.



These bipeds raise structures of hard earth or plant matter for shelter against the elements, draping themselves in softer materials for further protection.  They shape the world around them, but are more immutable, unchanging in form.  Different from the entity, in many ways.



This was the stage in the cycle when the entity is most aware, most focused.  It observes the possible worlds and judges which would be best.



\emph{Colony, }the entity voices the idea.



With that same signal, the various nuances suggest countless worlds that are to be removed from consideration.  Worlds without enough population.



\emph{Agreement}, the response comes.



The entity's counterpart is taking a passive role, investigating only to confirm, to validate.  This is concerning.  Where is the counterpart's focus, if not on this vital decision?



Study reveals worlds with dominant belief systems, peaceful worlds, worlds crowded with twelve billion individuals.  Worlds with almost none.



The entity pares through these, deciding.



It investigates, and in the doing, it prepares some shards for analysis and understanding of this particular society and culture.  Language, culture, patterns of behavior, patterns of society.  This is something the counterpart should be emphasizing.



The process is interrupted by an arrival.



A member of their own species, approaching.  It was smaller, took a different form.  It used different means to travel.



This was what had distracted the counterpart.



Its ancestors had traveled a different path, easily hundreds of cycles ago, before the entities had begun traveling in pairs.  This new arrival had encountered different worlds, less worlds, and it had developed differently.



The lesser one crossed paths with the entity's counterpart.  For a duration, they intertwined, meeting through multiple realities, their bodies rubbing and crushing against one another.



A sharing of details, a wealth of knowledge, from hundreds of cycles.  A sacrifice of the same.



The lesser one moves on, bloated with new shards and knowledge, but the counterpart flounders.



It sacrificed too much.



\emph{Concern.}



\emph{Confident.}



The counterpart is not worried.  The signal carries notes of hope for the future.  The counterpart will replenish its shards, its stores of knowledge, memories and abilities at the conclusion of this cycle, reuniting with the entity.



The counterpart is supposed to be the passive figure, the thinker, the planner, while this entity is the warrior, the protector.  The entity is forced to make up for the counterpart's disability, to slow its advance through the void as they approach their destination and devote resources to analyzing, something the other should be doing instead.



The focus is on one reality.  They will subsume it first, then expand to others.  The most efficient route, achieving maximum amounts of conflict.  By testing their own shards against one another, they gather information.  The entity's shards will fight among each other, and they will fight the counterpart's, and they will steadily learn.



With a species such as these social bipeds, the entities can draw new conclusions, come up with new uses for shards.  It tracks and records details that allow it to shape new shards at the cycle's conclusion.



But their new hosts are a weak species, fragile.  The abilities must be limited in scope.  Worlds that are too advanced would be too fragile, as advanced weapons eliminate too many, cut the process short.



\emph{Destination.}



\emph{Agreement}, the response is not so complex, is expressed in a softer, quieter manner.



Still, the pair have settled on a set of realities.



The entity focuses on one.  Enough individuals, natural conflict and confrontation.  A balance of physical and emotional stressors.  The environment is damaged, but not so much it would inhibit growth.



\emph{Hive}.  The entity communicates the decision.



\emph{Agreement}.  The counterpart grasps it immediately, knows which reality he means.



The focus changes.  An interplay of communications, one bouncing off the other, as they designate realities.  Each shard needs one, some shards need to cluster and reside across multiple realities.  They draw on these worlds for power, for energy, and thus fuel the techniques they have been coded with.



Each shard, in turn, needs a target.  The entity's focus expands, designating likely partners.  Past mistakes have been accounted for, and the shards will connect in a covert manner.  They will reside in other worlds, uninhabited worlds, and they will remain cloaked and concealed in areas this new host species is unlikely to explore.



It is a negotiation.



\emph{Ownership here.}



\emph{Claim there.}



\emph{Territory here.}



With each statement, they each catalogue the realities.  Similar realities are included together, for both the entities and the shards.  Too many complications and confusions arise when interacting with worlds that are exceedingly similar.  Not an effective form of conflict, when it is the same lessons learned over and over again.  It is better to connect them into groupings, limit exposure to each set of worlds.  One shard is capable of settling in a \emph{grouping} of near-identical worlds, drawing energy from all of those worlds at once.



The entity looks to the future to check for danger.



\emph{Plague.}



All signs point to the shards murdering their hosts.



The hosts must be protected, or this will be disastrous, counter-intuitive.  The entity adjusts the innate safeguards, protections to reflect the host species and their tolerances.  The bonding process will protect the host, where the host needs protection.  Shards that are capable of providing flame at will cannot burn the hosts, now.  Shards are reorganized, combined and clustered where necessary, to grant sufficient protection.



\emph{Infestation.}



Better, but not perfect.  The entity refines the process, limits certain abilities, so they will not eradicate too many at a time.



\emph{Soft.  }The broadcast is sent out to the counterpart, along with suggestions and tips on how to refine the shards.



\emph{Agreement}, the counterpart accepts.



But the entity can still see fallout effects.  There are parallels in memory storage.  Not many, but there may be glimmers where the subject is capable of perceiving the information stored in the shard as the connections are formed.



For good measure, the entity breaks up one shard cluster, tunes it, then codes the effect into each and every shard.  It studies the host species further, refines, attunes.



It takes time, but the entity forms a sufficient safeguard.  The host species will forget any significant details.



The broken shard is cast off, joining countless others.  It will bond to a host.  The entity looks forward, checking.



After the target planet has revolved thirty-three times around its star, this shard will connect to a host.



A male guards his offspring, a female, with his size and bulk.  A group of hostile bipeds cluster around them.  They call out, making unusual loud sounds, suggesting intoxication.  One of the hostile ones gestures, gripping its male parts, pulling them free of their coverings.  A sexual gesture follows, waving the organ left and right, thrusting it into the empty air.



Sounds of amusement, laced with hostility.



The male and his offspring retreat as far against the nearest construction as they are able.



The shard connects, attaching to the male.



No.  It is ineffective.  The female is clearly more distressed.



\emph{Prey}.



There is a way to maximize exposure to conflict.



The entity taps into its understanding of the bipeds and how they operate, recognizes the signs of distress, the nuances such things can have.



It views the future again, with changes made in the code.



This time, the shard settles in the male, then immediately shifts to the more distressed female.



\emph{Insinuation.  }The shard connects to the host's neural network.



The bond is created.



The shard opens the connection as the stress peaks, and the host doubles over in pain, bewildered, stunned.  The shard then forms tendrils that contact each individual in the area.  It retains traces of the entity's tampering, of the studies in psychology, awareness and memory, and is quick to adapt.  It finds a manner in which it can operate, then alters itself, solidifying into a particular state.  The remainder of the functions are discarded, the ones in the shard itself are rendered inert to conserve power, while the ones in the host fall away, are consumed by the shard.  The host's neural network changes once more.



The female disappears from the awareness of the hostile ones that surround it.



The entity looks to the future, to see if this is sustainable, efficient.



All seems well.



A view of other bondings suggests this emphasizes younger targets, particularly those in a middle stage of development, between a lesser phase and an adult phase.  Emotions are higher at that juncture, and the possibility of conflict increases further.



The entity allows for deeper connections to foster more conflict.  The underlying instructions are already present from previous cycles, and can be left largely alone.  These bipeds war with each other enough.  It will only serve to assist the most extreme cases.



\emph{Forget}.  The entity informs its counterpart of the changes it made.



\emph{Agreement}.  The counterpart acknowledges.



\emph{Emotion}.  More changes.



\emph{Agreement}.



Before the last response is received, the entity has already begun shedding shards that won't prove useful or particularly problematic.  Shards for attack and defense, distributed over an even geography, an even timeline.



More complicated shards require more focus.  Ones that harbor stored memory of technology and development in past cycles are prepared so they might bond with a host and transmit that knowledge.



For others, there is no easy way to apply the contained knowledge, so they are coded to draw from the host's recollection and awareness, or to search the entire planet for details and information on what it might be able to do.



Ones that alter the nature of the host in fundamental ways are planted throughout, so as to add more variables in how the others must adapt to them.  A host that chooses how gravity applies to it.  A host that can become a storm of friction, intensifying all friction in an area around it.  One that becomes immaterial.  Another that can make paths between realities, with safeguards to keep it away from ones the shards are rooted within.



The entity is approaching the galaxy cluster in question now, and it sees its counterpart doing the same, if at a slightly slower pace.  Both are trailed by a cloud of shards now, each cast off in such a way that it won't reach its target location until a set time and date.



The entities begin to close their spiral dance, drawing together as much as they can with the counterpart struggling.



They approach their destination, and begin to disintegrate in great quantities, until thirty percent remains, twenty, ten, two\ldots



It will take one hundred and sixty revolutions before their destination reality hits critical mass.



Three hundred and thirty-one revolutions before the shards reach a critical mass and enough information is gathered.  To look to the future and seek that information in advance would take too much energy.  To do this and fail would be a catastrophic setback in the cycles.



This suffices.  It spends the least energy for the maximum result.



The counterpart is descending, having selected a destination world.  It is hemorrhaging shards in clusters, due to the excessive exchange of shards with the lesser one, too soon before their arrival at their destination.  These shards are breaking off in huge volumes.



A check confirms these shards are coded, that everything is technically well.



\emph{Danger, }the entity broadcasts.



\emph{Confident, }the counterpart replies.



The counterpart remains secure.  Nothing to be done.



There is no more time to devote to the crisis.  The entity focuses on its destination, on the next part of the cycle.



The shards have largely been assigned to hosts.  They will remain latent, they will wait for the first crucial moment of crisis and use that to shape their function, to better assist their host.



It is impossible to check the exact circumstances for each event.  Some shards harbor particular concepts, and will shape their application to the host's needs.  Others are coded with particular applications, and will either scan viable realities or the host's frame of reference for how that application will come to pass.



Physical harm will grant physical assets, be it direct or abstract.  Immediate danger will nudge the shard towards defensive abilities.  Ranged attacks against living threats, an ability to shape or affect the environment against environmental dangers.



Successes will help refine the abilities, provide inspiration for the development of new shards.  Failures will help all the same.



In hosts, too, there will be variations.  The shards might seek out different hosts, if others are in range, as the perception-altering one did.  They will fragment and transmit to other hosts, as they grow and develop.



The entity is satisfied.  In terms of raw size, it is but a small fragment of what it once was, barely a cluster of shards now.  Its part in this phase of things is nearly done.



The next part of the cycle begins.



It chooses an unoccupied reality.  A barren planet.  Its perceptions focus on the landmasses in idle curiosity.  Different from the focus reality, but similar.



They have reached the solar system in question now.  They brush up against one another, and the entity shores up its counterpart where it can, sacrificing its own shards in the process.



\emph{Acceptance.  Gratitude}.



The counterpart's message is thin, but the entities are but a ten-thousandth of a percent of their original size.



It turns its attention to adapting.



In the course of thousands of cycles, the entities have refined their methodology.  There are no true points where they are vulnerable.



As the whole, as the entity, it is safeguarded by countless abilities, defenses, perceptions and options.  It is fat with the knowledge of every generation that came before, the mistakes, the problems, and the solutions.  While it travels the void, it is virtually untouchable.



But there have been times where the shards were vulnerable, after bonding with hosts.  Even now, there are dim possibilities that they might be rooted out.  There are issues where shards that have been coded to generate conflict could do too much damage, disrupting the cycle.



This is something that must be tended to.



The entity turns its attention briefly to their target reality, observes the various life forms.



Always, in the course of its examination of the possible futures, it was evaluating, checking to see what was necessary.



A quick glance into the future, not so deep a look as to expend too much of its remaining energy.  Conservation is key at this juncture, and from here on out.



The entity's present configuration is satisfactory.  The chance the cycle can be interfered with has become infinitesimally small.



The shard that allows the entity to see the future is broken up, then recoded with strict limitations.  It wouldn't do to have the capabilities turned against the entity or the shards.



The fragment it just used is sent off, directed to a small female.



The other fragments in that same cluster are retained.  To see the future is resource intensive, but the entity will harbor it as a safeguard.



More abilities are used to check, investigate, and then cast off.   The ability to communicate and receive signals is unnecessary now.  To transmit signals across wavelengths.  It, too, is intentionally crippled as an ability.  It would not do to have that one being used with regularity.  Such would be distracting for the entity and its counterpart.



When it knows the configuration is absolutely decided, it reaches for the last fragment it will cast off.  This one, too, it cripples, even largely destroys, so as to limit the host from using it in the same fashion.



In a haste to decide matters before it enters the stratosphere of that barren planet, the entity casts it off to a similar location as the future-sight ability.  A similar time, thirty-one revolutions from now.  The destination is a male, thin, in the company of strong males and females, drinking.



And with that, the entity lands on the barren planet.



The planet revolves around its star once before the entity even moves.



The entity rises and extends its perceptions across multiple realities.



\emph{It's time.}



\emph{Chrysalis.}



The entity changes.



A star that burns twice as hot burns for half as long.



Not truly, but the entity is aware of the idioms and patterns of this world, is already thinking periodically in terms of the words and ideas of their languages, to frame thoughts for itself in this pivotal moment.  It serves to help codify the messages and intent.



The entities burn as hot as any star, with their sheer mass, their scale, the power they wield.  This is acceptable while traveling the void, when much of the body remains in a hibernation state.  Stored energy is expended as a resource, to view the future, to perceive and communicate.



But this is not sustainable here, in this phase of the cycle, when the entity is so much smaller.



The entity has cast off all but the most essential parts of itself, distributing the shards throughout this reality.  More shards will shower on other realities in time, likely around the point the first have started fragmenting in greater numbers



Cycle to cycle, the role changes.  Direct involvement, watching from afar, being visible or staying out of sight.  Different roles to shepherd the shards through different worlds.



The entity takes shape.  It retains the capabilities it had when it first arrived.



\emph{Imago.  }Adult state.



Much of it is still too large for the target reality.  It leaves that portion of itself behind, maintains a connection.  A safeguard.  The body it uses is but an extension, a tendril.



It codifies the thoughts and memories of the society it investigated into a usable fashion.



Then it waits.



\emph{Sentinel.}



Time passes.  A revolution of the planet around its star.



Something has gone wrong.  It is time, but it has not received a broadcast from the counterpart.



The entity emerges, stepping into the target reality.



It can see its shards showering down from above like meteors traveling the void.   The first to arrive.



It can see the shards of the counterpart.



Not all are intact.



Dead shards.  Damaged ones.  Vital shards, even, going to hosts.



The entity destroys these on sight.  They are corrupt, ruined.  They will fail to provide usable results.



Extending its perception over the world and other realities, the entity can sense everything at once.  It can sense conflict.  Wars.



It remains aware of its limited lifespan.  Three thousand and six hundred revolutions.  To search like this costs a tenth of one revolution's time.  There is more than enough remaining before the cycle concludes.



Or there \emph{should} be.



The entity abandons the search.  Enough information has been obtained for it to know.



The counterpart is dead.



For a very long time, the entity is still.  It does not move, and instinctively holds back every ability, as if conserving energy in the face of a vast threat.



But this is not a threat that it can weather, like a storm of acid rain: The cycle has been disrupted.



Worse, it is terminated.  The entities have altered themselves so that each half of a pairing serves part of a role.  It is only with the counterpart that it can gestate, that it can modify the individual shards, cast the next generation out and start the cycle anew.



In seeking to understand the host creatures, the entity had coded shards to emulate them.  It is those same shards that experience the entity's first ever emotion.



\emph{Crushed.}



The entity comes to experience a deep, profound sadness, for the very first time.



Time passes, as the entity considers the ramifications.  The sky grows dark, then light again.  Dark, then light.



A structure, a vehicle approaches.  A hull pierces the water as it draws nearer.  A crowd stands on the uppermost surface, gathering.  They stare, even babble among themselves, their voices jumbling together, a hum, a blur.  He can see into the other realities that lie adjacent to this one, similar people, similar crowds.



\emph{Drone.}



\emph{Buzz.}



They are communicating, and the entity is unconcerned.  It watches as they draw close to the edge of the vehicle, pressing themselves against the barrier that was erected at the edge.  They reach out.



They worship him.  Of course they do.  His form was crafted to fit the values of this reality.  They hold faith, and the entity chose a shape that fit the most celebrated figures of the most popular faiths.  Race divides this species, so the entity deliberately chose a form that didn't fit any one race, with skin and hair given the color and texture of another thing they celebrated and worshipped – a mineral.



This is intentional.



The entity sees a shard already taking root in one of the vehicle's passengers.  One of the dead shards, damaged.  The entity's vision allows it to see the man's inside, the damage.  He is dying of a systemic issue in his body, producing the wrong type of cells in the wrong places.



The entity reaches out, feels others touch his hand before the male finally makes contact.  A simple wavelength serves to kill specific cells.



The shard will grow now, damaged as it is.



With that, the golden man turns from the crowd and flies away.



\blacksquare



The Entity slowed as a figure barred its path.  A female, with her arms outstretched.  Smaller life forms were arranged around and behind it.



Vaguely familiar.



``Stop, Scion,'' the female said.



The entity came to a complete stop.  It could see the connection to the female's shard, the activity as it broadcast signals, reaching out to contact lifeforms throughout the area, coordinating them.



All around the entity, there were shards in varying states of maturation.  The female's was among the most mature.  Seasoned by conflict, heavy with information, lessons learned, tactics, applications, organization.  It had already fragmented once, heavy enough with information that it could afford to handle other roles.  The fragment would have a derivative ability, and given proximity, it would hopefully remain close enough to exchange information with the shard that it had split off from.  There were no signs of that exchange.  The female had separated ways from the fragment.



The entity recognized her shard.  The last one that had split off before the entity took on this form.



\emph{Queen.}



The entity's despair deepened for a moment.  It was a good thing that the shards were harvesting such good information, but nothing would come of it.  The cycle had been disrupted.



``I know you want to help, but it's too dangerous.  You're too strong, and this situation is fragile.  It'll do more harm than good.''



\emph{More harm than good}.  Scion accepted that as a given and decided to stay where he was.



The female kept on talking as memories stirred.



\blacksquare



A male approached.  No shard, no powers.  The area was dark, the planet turned away from its star.  The entity was hovering over the highest point of a short bridge that spanned a river.



\emph{Lost.}  It had created itself for a purpose it could no longer fulfill.



The male pulled off one foot-covering, hefted it, then threw it.  It bounced off the entity's face, not even eliciting a blink.



The male hauled on the other foot-covering, but it was too tightly bound.



He gave up, half-hopping, half running up the length of the bridge, pounded his fists on the entity's chest, scratched, clawed.  Aggressive actions, but it didn't matter.  The entity was invulnerable.  It could glance into the immediate future and know there was no potential reality where this male would be able to harm it.



Not that it mattered.



``Damn you!'' the male cried out.  ``Fucking perfect golden man!  Fuck you!  Just\ldots just bleed!  Fucking feel this!''



A strike to the entity's face.  The male nearly fell from the bridge.  The entity would have let him.



``You don't- you don't deserve this!  This power!''  The male sniveled, mucus running from his nose.  Flecks of spit dotted his lips from the sheer force of his words.



``They keep saying you're fucking sad!?  What do you have to be sad about?  You weren't beaten black and blue by a fucking girl you were too chickenshit to hit back!  You haven't been kicked around by motherfucking teenagers who thought it'd be good for a lark!  Buggered against your will\ldots no!  You get to be untouchable!''



The male clawed and scratched, long dirty fingernails scraping at the entity's body, clawing at a nipple, at the part the entity had crafted to look like genitalia.  Nothing did any harm.  Even the dirt skidded off, failing to find any traction in the entity's skin.



The male collapsed, his face pressed up against the entity's chest.  His mucus and saliva slid off with the same ease the dirt had.



``Fuck you.  Fuck you, golden man.  You don't\ldots you don't deserve to be miserable.  Or you don't deserve to be miserable and useless.  Fucking burden on society, distracting people from shit that needs doing.  Fuck you, you ponce.  You\ldots Fuck you!  Go do something.  Never got that.  All these sad fucks that kill themselves or hide away\ldots if you're going to be miserable without a damn excuse, go to Africa and help those damn kids who were orphaned in wars.  Go\ldots save people from burning buildings.  Help clean up after disasters.  Work in a fucking soup kitchen or something.  I don't care.''



The man's voice had gone quiet, barely more than a whisper.



Another pound of fist against the entity's flesh.



``I don't care if it's penance or if it's a fucking way to kill time.  Do some goddamn good, and maybe you'll feel like you're worth a damn.  Maybe you'll stop being so fucking miserable.''



The entity continued to stare out over the city.  It absorbed the words, considered them.



It was a task.  A role it could play.



It was something.  What had this male said?  Which were ones the entity could achieve?



Save orphans in wars.  Rescue people from burning buildings.  Clean up after disasters.



The entity took flight once more.



\blacksquare



The entity remained patient.  Patient then, patient now.



``\ldotsYou could go to Houston or New York, even.  That's far enough away from Jack,'' the young female with the administration shard was still speaking, quiet, intense, urging without prodding.



The entity and the young female were still hovering over what was becoming a major site of conflict.  The entity extended its senses over the area.



At the center of it all was a man.  Not at the center, but everything tied to him.  Everything moved in relation to him, and he moved in relation to others.



The entity stared, intrigued.



``\ldotsWe can't stay here.  Come on.''  The female host was still talking.



The female paused, waiting.



``Orrrr you don't understand what I'm saying.  Or you don't care.  Fuck me.  Listen to me, Scion.  Pay attention.''



The entity turned its attention to the young female.  Its hands found the entity's, pulled.



There was a meaning behind the gesture, but the entity was too lost in observing what was going on below to care.



A confrontation had started between a young male and an older one.  A fragment of a shard against a very mature shard.  The most mature shard in this area, at a glance.



The more mature power was unleashed.  A wavelength power, a kinetic transmission.



The entity watched, and it recognized the shard at work.



The broadcast shard.  One that had been crippled, just like the shard of the female that floated before the entity now.  The same shard that had managed communication between the entity and its counterpart.



The entity turned to observe another conflict.  One shard was connected to eight individuals.  A lesser shard, connected to eight unusual hosts.



The eight advanced in clusters, moving towards the various individuals that seemed to be hostile to them.  The shards connected to each individual provided more detail than anything else.



``You big golden idiot!  Come on.''



Her subjects formed a thick cloud, blocking the entity's vision.  No matter.  It could still perceive the world.



``Come on!''



She pulled harder.



The entity turned to follow the confrontations.



The male with the broadcasting power was swinging his sword.  The younger one was erecting defenses, lashing out.



Their shards were reacting.  The entity could see how every aggressive shift in the younger one was met by an instinctual retreat in the older.  Cause and effect, invisible but there.  The nature of the shifts changed as they started speaking.



To strike the one with the mature passenger was akin to trying to catch a leaf in the wind.  The hand moved the air which moved the leaf, and it slid just out of reach, just beyond the hand's grasp.



Ah.  There.  A narrow miss.  The male slid out of reach, and he prepared to go on the offensive.  His shard shifted, just as ready and able to capitalize on the weakness in offense as he was able to evade trouble in defense.



A shard flared to life, and the entity saw an effect take hold around it.  It reached out and found a barrier it could not penetrate.



\emph{Cell}.



Its hand was moved back to the previous position.  It was caught in a sinkhole of distorted time.  Over and over again, it moved in a steady loop.



\emph{Snare}.



A trap.



\blacksquare



The city burned, and the entity wielded its power.  Controlled wavelengths disrupted the molecules, extinguished each source of heat, inside and out, rendering it a little cooler than the ambient temperature.



Countless individuals fled for safety, running in droves.  The entity watched, but it did not rest.



It hadn't rested in years.  The longest it had stood still was in the company of Kevin Norton, where the man gave it a white covering that clung to its body.  As instructed, the entity kept the cloth clean, pushing out energy in patterns and yields that would drive out the soil and smoke while leaving the cloth intact.



It lowered itself to get a better angle on one blaze in the basement area of a library.  In the doing, purely by accident, it lowered itself to eye level with a female on a balcony.



The female was startled, afraid, unable to even breathe.  It could look inside the female and see the emotions as an increased heart rate, hormones and adrenaline churning through her system.



It almost blurted out the words.  ``\emph{Kto vy?}``



The entity understood the Russian words as it understood all languages, through the knowledge it had scanned for and codified, prior to arriving.



It remembered the instructions Kevin Norton had provided.  To be polite, to be considerate.



Speaking, nonetheless, was an unfamiliar concept.



How to answer?  The entity did not know what it was.  It had no role but the one ascribed to it by Kevin Norton.



In thinking of the man, the entity thought of a thing the man had said.  A word in the midst of a story about ill-behaved spawn.



As it did most words, the entity had searched its memory for details on the concept.



\emph{Zion}.



A promised land.



A utopia.  A harmonious kingdom.



The promised land could be this world at its climax, the shards at critical mass, the entity and its counterpart bringing about the end of the cycle.  It could be utopia, as the entity understood the term.



It could be the world at peace, people saved from hardship, as Kevin Norton had described it.



Whether the entity was somehow able to return to its original task or whether it continued carrying out Kevin Norton's answers in an attempt to find itself, the term fit.



``\emph{Zion},'' it spoke.



\blacksquare



Memories.  A refuge, a reminder of how things \emph{should} be, if the cycle were intact.  There would be more shards, more conflict, but it would be more controlled.  The dead shards polluted the setting, almost too numerous.



The female with the administrator shard had long since fled, covering the retreat with her small army of lesser lifeforms, more traps snapping into place in her wake.



It thinks of Zion, and it thinks of other metaphors and ideas.  In the thirty-three revolutions since arriving on this planet, the entity has had time to think.  It has saved a lot of individuals from harm, heard many prayers.



It was aware of everything that occurred around it.  The planet's star moved across the sky, above the dark, heavy clouds of moisture.  Small movements, but movements nonetheless.



It thought of the beetle in one mythology, rolling the orb across the sky.



It was an idea that persisted across mythologies.  \emph{Scarab}.  \emph{Chariot}.  The Brother.  The Sky Barge.



Abstract thought.  Was that the sort of pattern that led to a connection, an inspired idea in the development of new shards?  The entity wasn't sure.  Its counterpart was supposed to handle such matters, retain that capacity for thought and analysis.



Its physical body continued to loop in time.  It didn't matter.



The conflict continued.  The broadcaster was moving in and out of trouble, relying on a pronounced projection that was being emitted by a dead shard to provide further protection.  There was another entity nearby.  A boy with another dead shard.  Odd, that they had gravitated towards the broadcaster.



Mature shards, a situation ripe with conflict, so much to be gained, and nothing could be done with that.  The entity felt a hint of another emotion, dismissed it.  The simulation of the host-creature's psychology was only that.  A simulation.



It would spend some time here.  Nothing would change in any event.  Kevin Norton had passed.



The entity observed the ongoing conflict.  No less than five seconds after it had been trapped, two figures had emerged from a doorway between worlds.  The entity could see the paths forming, trace them back to the source.  Another world, a living world without a shard occupying it.



They engaged the eight with their own perception abilities, intervening to assist a group of others.  As a pair, they opened fire with guns, then waded into hand to hand combat.



The entity looked at the male, and it saw the connection to the same shard as the eight.  His connection was stronger, more mature.



It looked at the female, and it saw a shard that wasn't its own, but wasn't dead.



\emph{Puzzling.}



The fight progressed.  Strikes with weapons and with the creature's limbs were evaded, a careful dance of attacks where each edge and bludgeon touched skin, many even shaving off the finer hairs from cheeks, noses and chins.



The male fought the eight in such a way that they couldn't move without exposing themselves to attacks from the female.  Each movement placed the male in a path for obvious harm, a fatal blow, but the eight could not capitalize on that.  At the same time, he positioned himself in such a way that four or five at a time were unable to retreat.  Not just in reach of weapons, but in reach of arms, elbows, for being taken hostage.



The female felled three of the eight, and the situation was decided.  The remaining five dropped to a position where they sat on their knees.  She spoke, and an interdimensional portal appeared behind them.



They crawled through, heads down, and the portal closed.



The pair glanced up at the entity as another wormhole opened.  They stared.



The entity, in turn, faced a different direction, but it could perceive them nonetheless.



They disappeared back into the portal.



Puzzling.



The entity observed as the fight concluded elsewhere.



The broadcaster remained unaware as an individual without any attachment to shards at all entered the confined space, unloading a vaguely familiar substance over the group.  Something the entity might recollect if it had access to all of its memories.  A technology.



It didn't matter.



The entity watched as the broadcaster was sealed in a time distortion.



A female, standing just outside another time distortion, walked around the effect, charging objects with energy.  The entity could see as the small pieces of alloyed metal unfolded, taking shape in not just this world, but \emph{all} realities, at the same space and time, bristling with an effect that would sever their attachment to most physical laws.



They were thrown, and they disrupted connections to two shards at once.  The projection disappeared, only to reappear a distance away.  The boy who had created the time distortions fell as well.



\emph{Sting, }the entity thought.  Once it had been a weapon for his kind, against his kind, back in the beginning, when they had dwelt in oceans of gray sludge.



The others hurried to confine the broadcaster.  They were apparently aware of what he could do.



\emph{Interesting.}



\blacksquare



``Just you and me,'' Tecton said.  ``That's what he said.  Between gasps of pain, anyways.  `I wish I had better company, but I'll take what I can get.  Ironic, that you're so \emph{boring}.''



Golem looked at his old leader.  ``That's it?''



Tecton shook his head.  ``He said, `I bet you think you're noble.  You're not.  You're uglier than any of us, \emph{sparky}.''



``And?''



``And that's it.  The D.T. guy foamed up the gap, I raised the shelf, you closed the hand, and he was completely sealed in.''



``You're right.  That doesn't make a lot of sense.''



``He hasn't ever \emph{met} me.''



Golem shook his head.  ``Doesn't seem world ending.''



\blacksquare



``\emph{\ldots}\emph{I }always hated the blank\ldots \emph{slates,'' }Jack groaned the last word.  His utterances were finding an odd cadence or rhythm between the gasps of pain, the fresh wounds that were actively criss-crossing his body, opening his stomach, his intestine being gripped and pulled through the wound as if by an invisible force.



The foam weighed him down, and in the midst of the complete and total darkness, he stared skyward.



``\ldotsNever that \emph{interesting}\ldots''  He grunted.  ``Never created \emph{art}, \emph{never}\ldots created \emph{variation..}.  you're worse \emph{than}\ldots most\ldots''



High above, the entity listened.



\blacksquare



Tattletale listened over the earbud microphones as Tecton finished relating Jack's statements.



She raised her eyes from the computer.  Her underlings were arranged around the room, along with others.  Her soldiers were at the ready, alongside Imp's Heartbroken,  the first and second in command of the Red Hands, Charlotte, Forrest and Sierra.



Sierra was bouncing her leg nervously.  She'd cut off her dreads, and her hair was short to the point of being in a buzz cut, with a fringe flopping over one side of her forehead.  But for the hair and two small hoop earrings in one ear, she was a businesswoman.  Had to be, when she was the ostensible owner of all of Brockton Bay's prime real estate.



Charlotte was in the company of one of the children, holding him close.  Her fingers toyed with a paper origami cube, and she was doing her best not to look like she was poised on the edge of her seat for any news at all.



The \emph{second} she gave the word, they'd be ready to evacuate the city, to get people onto the trains and moved through the portal.



But\ldots



``Things have settled,'' she said.  ``Jack is contained.''



She could see them all relax as if strings that had held them rigid had just been cut.



``That's it?''



``I don't know,'' Tattletale said.  She grinned wide.  ``But if the world \emph{is} ending, then it's an \emph{awfully} quiet end.''



There were chuckles here and there, nervous relief.



``Go home, or go do whatever,'' she said.  ``I'll be in touch with more news, let you know how your territory leaders, past or present, are coping.''



As a crowd, the others began filtering out.  Sierra stayed where she was, pensive, but the nervous bouncing of her leg had stopped.



Charlotte, too, remained.



``Sup?'' Tattletale asked.



``It's him,'' Charlotte said.



``Aidan.  Hi Aidan.''



``He triggered yesterday.  It\ldots didn't take much.  Which is probably good.''



Aidan hung his head.



``That's excellent,'' Tattletale said.  She looked at the seven year old.  ``How are you?''



``Okay.  Had a nightmare for the first time in a long, long time.  I woke up and I was sleepwalking, and I didn't know where I was\ldots I got scared, and then it happened.''



``What happened afterwards?'' Tattletale asked.



``Birds.''



``Birds.  I see.  \emph{Interesting},'' she said.  Her eye moved over to the boards that marked the perimeters of the room.  Each was packed with information in her small, tight, flowing handwriting.  Messy, but she'd gotten good at putting pen to paper these past few years



``I \emph{push} and the birds go where I pushed.  Or I pull and they fly away from that spot.  It's hard to do.  I can see what they see, but not while I'm controlling them.''



``Like Taylor, but birds, and not that flexible.  I \emph{see}.''



``We suspected he would trigger,'' Charlotte said.



Tattletale looked up, surprised.



``Aidan had a dream one night, back when the nightmares stopped.  He drew that picture.''



``Picture?''



``I gave it to you.  I kind of emphasized it might be important.''



``Pretty sure that didn't happen,'' Tattletale said.  She stood from her desk.  ``Sorry, Aidan, to squabble in front of you, but Charlotte needs to remember I don't tend to miss stuff like that.''



``All that money you've given me for helping to look after the territory?  The money for the kids?  I'd stake it all on what I'm saying now.  I promise, I \emph{swear} I handed you that picture.''



Tattletale frowned.



``I swear,'' Charlotte said, for emphasis.



``Then there's a fucked up stranger power at work.  Don't like that idea.  Let's see.  Um.  I store everything in a rightful place.  If you handed me a picture\ldots was it \emph{here}?''



``Here.''



Tattletale crossed the room.  She pulled a bin off a shelf, then sorted through file folders.



Charlotte said, ``There.''



Tattletale stopped, then went back a page.



``Huh.  I stand corrected.''



There was a beep on the computer.  Tattletale went back to the computer to investigate, shrugged, then sat down.



``Well?'' Charlotte asked.



``Well what?''



``The \emph{picture}.''



Tattletale frowned.  ``\emph{What} picture?''



``What's going on?'' Aidan asked.



Charlotte stalked over to the bin that was still out, grabbed the paper, then slammed it down on the desk.  ``I don't think a piece of \emph{paper }can have superpowers.  Pay attention.  Focus  Memorize.''



Tattletale frowned.  She turned her attention to the paper.



There \emph{was} a block there.  She felt it slide out of her mind's eye, caught herself.



She turned her attention to the surroundings, the underlying ideas.



``Aidan?  Describe it to me.  I don't know what you drew.''



``Those are kind of like fish, or worms, or whales, but they fold and unfold in ways that are hard to understand, and there's stuff falling off them.  Those are stars, and-``



Tattletale felt something fall into place.



As though a floodgate had opened, the pieces started coming together.  She stood from the desk, striding across the room.



There were still gaps in her work on the boards, where she was outlining everything, trying to decipher the underlying questions.  Now, she began unpinning things from the board.



She was remembering, and she was putting it together, now.  There was a block, but she'd formed enough connections now that things were going \emph{around} the block.



\emph{The whole}.  The idea had stuck with her.



All powers fed back into a greater whole, each was a piece of a greater construct.



Of Aidan's fish-whale-worm things.



But that wasn't it.



No.  It didn't fit in terms of timeline.



There was more.



``Like gods,'' she said, recalling.



``Like viruses, like gods, like children,'' Charlotte said.  ``Back on the day I first met you, you said that.''



Like viruses, infecting a cell, converting it into more viruses, bursting forth to infect again.



Like gods.  So much power, all gathered together.  All powers stemmed from them.



Like children.  Innocents?



\emph{Blank slate}.



``Oh,'' Tattletale breathed out the word.



``Tattletale?'' Sierra asked.



``Oh \emph{balls}.''



\blacksquare



``I'm \emph{not}\ldots \emph{Darwinist,'' }Jack gasped.  ``None of that\ldots \emph{bullshit}.  Augh!  I'm\ldots I think it is simple-``



He continued grunting.  His switch to turn off the pain took a second to activate, took deliberate action, but getting in the rhythm meant he could buy himself one or two seconds of relief with each loop.  It was a question of concentration, and his concentration slipped.



``It's \emph{simpler}.  Us monsters and\ldots  \emph{psychopaths}, we gravitate towards\ldots \emph{predation}, because we were originally\ldots \emph{predators}.  Originally had to hunt\ldots  Had to be brutal, \emph{cruel}\ldots''



He paused, spending a few moments grunting in pain, letting the loops continue.



``Order to survive.  Violence was what \emph{made us}\ldots or\emph{ broke us back\ldots }in the\emph{ beginning}.''



The entity was patient.  It had time to spare.



\blacksquare



Saint swayed slightly in his seat.



The information continued to stream in along a dozen different channels.



Too much.  It was too much, but somehow, somewhere along the line, they'd succeeded.



Jack was contained.  Things were quiet.



Until he noted someone bludgeoning their way through Dragon's password security.  A series of personal questions, ranging from a favorite \emph{texture }to something about a pet name for Dragon to a question about the first results of the ten by ten game.



The first two were answered in order.



\emph{Defiant}?  \emph{Getting access to the system?}



No, too crude, too obvious.



The individual stalled on the last question.



He waited a few long moments, then saw the same individual making calls to Defiant.  Three communiques, initiated within one or two seconds of one another.  Then emails, to the PRT and Defiant both.



Saint intercepted it.



``\emph{Fuck, finally!''}



``What are you trying, Tat-``



``\emph{Shut up and listen, douchestain.  It's Scion.  He's the point where it all catalyzes!  And I just clued into the fact that he can probably sense Jack!  Get Grue back to the area, blanket Jack in darkness, }\emph{now}!  Now, now, now!''



``Mags!'' he shouted.  ``Dobrynja!  Get Grue back to the scene \emph{now}!  This is it!''



``On it!'' the reply came back.  There was a pause.  ``Grue is four miles away!''



``Teleporter,'' he said.



``We don't have any that survived the last few Endbringer fights!''



Saint hesitated.



Too far, it would be too late.



The woman who claimed she could control Scion.



His tired fingers flew over the keyboard.  He dug up the file.



It had been seen to.  They'd taken her name, but there'd been no proof.  Hearsay.



Hearsay was better than nothing.



The cyborg was piloting the closest Azazel.  Controlling it could be seen as an attack.  The cyborg would fight, wrestle him for control.



He opened up the window for a message, instead, even as he used the full access Dragon had for every camera, email and phone message to find this \emph{Lisette}.



A Hail Mary, if there ever was one.



``Defiant,'' he said, overriding everything in his way to open communications with the cyborg.  ``Help me.''



\blacksquare



The entity followed the movements of the various individuals around the battlefield.  More containment foam was being layered over the broadcaster, burying the area.



A noise, a blare that had people doubling over, covering their ears, started emanating from one of the craft.



The craft launched a second later, flying right for the time distortion.



It crashed into the area of warped time, wrapping forelimbs, tail and rear claw around the irregularly shaped feature.



The blaring noise stopped as a voice emanated from the speakers.



\emph{``Scion.  Zion.  Golden Man.  It's Lisette.  Kevin Norton introduced us.  What the man down there is saying\ldots whatever he's saying, don't listen.  Turn away.  Please.}``



\emph{Turn away.}



The entity moved, and it broke through the time distortion effect with ease.  The craft fell head over heels before propulsion kicked in.  It had to fly in zig-zags to keep pace with the entity's slow retreat from the scene.



``\emph{I- uh.  You broke free.  Okay, good.  Leave.  Run!  Please go.  I'm- I'm so sorry I wasn't able to talk to you before.  You never came back to that spot, and I could never reach you to talk to you.  There was help you needed and I couldn't give it.  I went to authorities, and nobody believed me.  But now, now maybe I can give you advice.  We can work on this together?  As a pair?  Is that alright?}``



The entity didn't respond.



``\emph{I hope it's alright},'' she said.



The entity took flight, leaving it all behind.



\emph{Leave.  Run}.



It didn't return to the task of saving lives.  For a period, it only flew.



It stopped when it had circled the world twice, hovering over the ocean where it had first appeared.



The broadcaster had finished speaking just a moment before the craft had launched, oblivious to the blaring noise that had been intended to drown him out.  \emph{What I don't understand, is why a blank slate like you would default to doing good deeds, rescuing cats from trees.  Why not turn to that violence, as our ancestors did?  It drove them, just like it drives the basest and most monstrous of}\emph{our kind}.



Had he known he had a listening ear?  Had it merely been a struggle to continue doing what he'd instinctively done for decades?



The shards retained memories, motivated, pushed.



The entity looked to the future, looked to possible worlds, and it saw the ways this could have unfolded.  It burned a year off of the entity's life, but he had thousands to spare anyways.



There was a scene where the entity stood over the broadcaster's corpse and ruminated on what had driven the male to such extremes.  The shard wasn't a particularly aggressive one.



A scene where the man died, and years passed, the entity slowly coming to the same conclusions as it observed the rest of the species.



The entity had done good deeds for years, at Kevin Norton's suggestion, waiting and hoping for the reward, the realization.  When none had occurred, it had simply kept doing what it had been doing.  Seeking out alternatives wasn't even in the realm of imagination, because imagination was something it lacked.



It had power, though, and if either the counterpart or the cycle had been intact, they could have filled in for that imagination.



Still, it could experiment.



It gathered its power, then aimed at the nearest, largest population center.  Kevin Norton's birthplace.



The golden light speared forth, and the island shattered, folding, parts of it rising from the ocean.  Crumpled like paper in a fist.



The entity did not eliminate the smoke or the waves that followed.  It simply let the aftermath occur.



The simulated human mind within the entity felt a glimmer of something at that.  Pleasure?  Relief?  Satisfaction?



Something deeper inside, something primal, tied to memories back in the beginning, \emph{before} the beginning, responded in a very similar fashion.



The entity extended its perceptions outward, felt the reaction, the outcry.  It turned words around in its head, as if it were broadcasting to itself.



\emph{Scourge}.



\emph{Extermination}.



\emph{Extinction}.



That last one was the one to fit.



An interesting experience.  After so much focus on the species as a whole, the evolution and development of the shards, on the \emph{cycle}\ldots



In this, it almost felt like it was evolving as an \emph{individual}, moment to moment.



The entity opened fire once again, and this time it struck out at the coastline on the opposite side of the ocean.





