





Just because I was miserable wasn't any reason I should inflict that on my followers.



A solid sixty or so people were gathered in a loose circle.  The roads were impassable, so we'd set up in the middle of an intersection, piling concrete blocks onto one another with a metal rack at the midway point.  A hole in the bottom let us feed the fire, and the pots we'd placed inside contained pork shoulders in baths of beer, carrots, onions and garlic cloves.



The smell had drawn people here from across my territory.  The temptation offered by the block of beer, soda and candy that was wrapped in plastic and sitting on a nearby pallet didn't hurt either.



Charlotte and the group of older kids I'd assigned to keep people from pestering her were handling the food.  Sierra sat on top of the pallet of supplies, making sure that everyone got \emph{one }beer at a maximum.  I'd assigned two people to guard her, but it was almost unnecessary.  Anyone here was either aware that I would stop them if they tried or they would have friends to warn them.



On another day, I might have made people get back to work.  The pork shoulders would take four or five hours to cook, and I didn't want to give up a whole day of good weather while people hung around, waiting for the moment things were served.  I left them be.



Coil knew what we were up to, and he'd shut down Tattletale.  Dinah felt out of reach, and my hopes of regaining some connection with my dad had ended less than perfectly.  Not badly, but not as well as I'd hoped.



Hope wasn't lost on either count, but I felt pretty low.



\emph{This}, right here, was the one thing that I could feel good about.  My people, my territory, doing something to rebuild.  Maybe I could have cracked the whip, but I'd rather they were happy.  It would do more in the long run, even if it meant less work got done.  They'd be dicking around waiting for the food to finish, and wouldn't get anything done tonight, after I gave them less restricted access to the beer and wine I'd had Cranston deliver.  Probably less in the morning, too, now that I thought about it.



Which was fine.  Coil had ordered us to expand our territory and deal with threats.  The people in my territory had cleared enough space for people to sleep, to store necessities and tools, enough that if twenty or thirty new people decided to work for me in the next twenty-four hours, I had space for them.  Expanding my control beyond this point would be a staggered process with phases of clearing followed by phases of settling.  There was no point to going the extra mile to clear more space if neither I nor my enemies would be occupying it before his deadline.



He'd specified three days.  We'd taken one to deal with the Chosen, I'd used the next to talk things over with Parian and visit the mayor.  We were officially done tonight or early tomorrow.



My swarm informed me of a visitor.  I stepped away from the pallet that Sierra was sitting on.  It was a bit disconcerting to see how the crowd parted to give me a path.  In my first night out in costume, I'd seen the ABB do it for Lung.  How much of that was respect, and how much was fear?



Maybe they weren't so distinct when it came to supervillains.



We met in the middle of the street.  Grue was wearing his new costume, complete with mask, and the semiliquid darkness rolled off him to spread out over the ground, hiding much of his body.



I folded my arms.  Speaking quietly enough that the others wouldn't hear me, I murmured, ``Any problems?''



His voice was hollow with the effects of his power, ``Just checking in.  I expected a call after your job.  I had to get the update on how you were doing from Tattletale.''



``Sorry.''



``I \emph{also} heard about what the boss was planning.''



``Going to give me a hard time for going?''



``No.  I don't like it, but I understand you didn't have a choice.  Or you \emph{did} have a choice, but you weren't about to take option B.''



``Yeah.  Which turned out to be the right choice.  He was playing us, trying to send us a message without rocking the boat.''



``You've got a lot of stake in this.  You holding up?''



\emph{I should be asking if you're holding up}, I thought.  ``I'm dealing.''



``And dealing involves a barbecue?''



I glanced over my shoulder at the crowd that was watching us.  ``Building loyalty.''



``You don't think you're going over the top?  Being too nice?''



``They're working hard.''



``That's all?''



I almost shrugged, but decided to maintain my composure, look confident in front of my people.  I needed a better term for referring to them.  They were sort of employees, but that was vague.  Should I take the same approach Parian did, identify my territory somehow?  The residents of Spiderville?  The Bugwalk?  The Hive?



``No, not all.  I figured I'd go all out, as much for me as for them.  This is the only thing that I've got going on that I can really feel good about right now.''



``The \emph{only} thing?''



I looked up at him.  Oh.



``No, not the only thing, you're right.  Though I'm not sure exactly what we're doing or what we are.  Not like we're in a position to go out to dinner and a movie.''



My heart was pounding so hard I worried he'd notice.  This would be the moment he'd tell me he was having second thoughts, that it was a mistake, he'd been in a bad place.  Or would he go one step further and accuse me of taking advantage of him, get angry?



``I've wondered about that myself,'' he said.



``It's okay, though?  Us?''



``Yeah.  Definitely okay.''



\emph{What would my people think if they could overhear?}



``I know we can't exactly go out, but if you're okay with it, you maybe want to come by tonight?  We'll let my people celebrate a week of hard work and head into my lair, eat, watch a movie on the couch?''



``Okay.  Not sure if I can get away before dark, if I'm doing a serious check of my territory.  Imp's doing more than her fair share.''



``It's fine.  I- I'm not sure how to put it, so I'll be upfront about this,'' I told him.  \emph{Which is easier said than done}.  It took me a second to organize my thoughts.  ``I don't expect to be priority number one.  We have a job here.  I'm not sure what the boss is planning, or if we're still going to be doing this a few months from now, or even a week from now.  But I totally get it if the territory comes first.  Or if Imp comes first, or we have a job that interferes with our schedules.  We fit each other into the breaks.''



I caught a glimpse of his arms through the darkness as he folded them.  ``You can \emph{say} that, but I'm not sure it'll be true when it happens for the third time, or the tenth.''



``It's not set in stone.  If it doesn't work, we talk about it.  Maybe it's best we say whatever's on our minds, given who we are.  We're not the best at the social thing, you know?''



``I know.''  He paused, glancing away.  ``In the spirit of saying what's on my mind, I'm kind of wondering how your people would react if I kissed you right now.''



\emph{So glad I have the mask}.  I felt my face heat up in what would have been an embarrassing flush if anyone could see it.



I swallowed.  ``No.  Don't.  It's not that I don't want you to, but it would mess up their image of me.''



``I know.  That's the only reason I didn't do it.  That, and the masks would be hard to manage.  Can't really be spontaneous when fumbling to find a way to lift the mask up.  And the stuff on this mask kind of makes it hard to lift it up.''  He tapped one finger on the criss-crossing fangs I'd designed into the face of his mask.  It would make it rigid, hard to remove without taking the entire thing off.



``Something to fix for a future version.  You want to grab something for lunch?''



``I should be getting back.  There's some stragglers to deal with, and Imp's been going full-tilt long enough I think I should relieve her.''



``She's taking this seriously, huh?''



``Yeah.  I'd be happy about it if it wasn't so dangerous.''



``With luck, the danger will pass soon.''



``Yeah.  See you later?''



I opened my mouth to respond, then stopped as I felt a tremor.  ``You feel that?'' I asked.



``No.''



No, I hadn't felt it with my own body.  My swarm had sensed it.  A vibration through the area.



My bugs could scent exhaust.  The acrid taste of ozone, for the lack of a better explanation.  I honed in on it, and realized that one of the buildings near the edge of my range had a new addition on the roof.  It was big, like two eighteen wheelers parked side-by-side, with two more stacked on top, but all one piece.



``Shit,'' I said, as the general shape took form in my mind.  I wheeled around to look in the direction it had settled.  ``Trouble.''



Darkness billowed out around Grue, making him look larger.



My first thought was Squealer, but she was supposedly dead.  The other alternative\ldots \emph{Shit.}



``Listen up!''  I called out, augmenting my voice with my swarm.  Most of the crowd was already paying some attention to me, but my shout got everyone else to turn my way.  ``Threat incoming.  Stop what you're doing and clear out of here, that way!''  I pointed.



Some people started hesitantly heading the way I'd indicated.



``Now!''  I shouted.  The crowd began to move.  Sierra and Charlotte were among them, abandoning the food and the makeshift oven.  Sierra looked my way for confirmation and I gave her a tight nod.



I doubted that my people were in any danger like they'd faced with Mannequin or Burnscar, but I wasn't taking chances.



``Who?''  Grue asked.



``Pretty sure it's Dragon.''



She wasn't moving.  She'd settled on the tallest building in the area, not too far from where I'd started my costumed career, fought Lung and met the others.  She was large enough that her mechanical forelimbs could grip two corners of the building.  She lay there like a resting jungle cat or sphinx, head raised, slowly rotating to take in her surroundings.



``The timing couldn't be worse for this,'' he said.  He settled one hand on my shoulder and pulled me in the direction my people were running.  ``Coil wanted us to be done \emph{today}.  Now the heroes are making a move?''



``Retaliation for the mayor,'' I said.  ``We pushed things, now they're bringing in the big guns.  Maybe literally.''



``Plan?''



``No clue.''  I got my phone out and dialed Tattletale.  She picked up on the first ring, as I was clicking through the menu to put it on speaker phone.



``Dragon's here-'' she started.  There was a flare of static, not unlike the noise from an out-of-tune radio station, ``-don't fight.''



``Why?'' I asked, but the static flared up again as I spoke, and I couldn't be sure Tattletale heard me.  ``She's \emph{here}.  How is she there?''



``Hitting multiple territories at once-'' Whatever she said next was obscured.  It was getting worse, fast.  ``-fight and heroes come to back her up.  Run, hide.  Meet-''



Then she was gone, lost in the sea of static.  I waited for several tense seconds, hoping she would come back on the line.



``Skitter.''  It was \emph{Dragon} who spoke over the phone.  ``I'm cutting off communications.  I look forward to talking to you once you've been brought into custody.''



The phone died.  There wasn't even a dial tone.



``Oh hell,'' Grue said.



``Let's go.''



We'd been retreating, but we broke out into a full-on run as the phone cut out.



Dragon, for her part, made a move.  Metal objects the size of a beachball were filing out of the sides of her suit.  They floated in the air, spreading out in formations.  Dozens of them.



``She's trying to beat me at my own game,'' I said, panting, ``Minions.  Hate tinkers.  Hate tinkers \emph{so fucking much}.''



A collection of my bugs died all at once, the sphere dropping to the pavement below with a thud that the bugs could feel.



I'd encountered this before.  Armsmaster's electric pulse, the one he'd used with his halberd.



``And I \emph{really} hate tinkers who share their work.\emph{``}



As I glanced over my shoulder, I could see the drones flowing into the sky in waves.  I ordered Atlas back to my lair to keep him safe.  I didn't want to risk him, didn't want to get shot out of the air while flying and I wasn't able to bring Grue along, wasn't \emph{willing }to leave him behind.



Was this what my enemies experienced?  A vague feeling of dread as an unreachable opponent massed her forces?  I couldn't necessarily fight back against them and even taking down one drone was useless.  Five or ten more would be ready to take its place.



They were overtaking us.  Any time I gathered more than a handful of bugs together, a drone would obliterate them with a point-blank electrical charge.  That was the only thing slowing them down; they would spend their charge, fall to the ground and then rise again a few seconds later as they rebooted.



I got a better look at the drones as they approached.  Each was an identical black sphere with two wings like the blades of a battleaxe, the tips of one blade connecting with the other.  A camera with a red lens was mounted on a plate that roved across the sphere's outer surface, while another plate glowed in the same way Kid Win's antigravity skateboard had, always pointing toward the ground.



One passed over my head, then stopped, hovering in place a few feet above me as I ran.  I turned on my heel and shifted left, and it followed me unerringly.  I zig-zagged and failed to shake it.



``\emph{Attention citizen},'' it blared, in the same voice that I'd heard from the armbands during the Endbringer fight, ``\emph{For your own safety, drop to the ground and place your hands on your head.  You have ten seconds to comply}.''



``Fuck!''



``Here!''  Grue called out.  He was turned toward me, bent to one knee, his fingers interlaced, nearly touching the ground.



\emph{``Five seconds}.''



I ran towards him, setting my feet in the cup of his hands, while drawing my knife.  He straightened, heaving me up.  My timing was off, and I didn't manage to jump in time with the push, but I did manage to stay balanced.  As he lifted me, I raised one foot and placed it on his shoulder, using it as a foothold to lunge for the drone.  I stabbed my knife at the antigravity panel.



It raised higher into the air.  I missed by a hair.



``\emph{Failure to comply.''}



I felt the hairs all over my body stand to attention a second before it hit us.  It felt more like getting a truck dropped on me than I would have expected an electrical charge to feel like, but I could feel the not-unfamiliar sensation of snakes writhing across my body.



It had knocked the wind out of me, leaving me lying flat on top of Grue.  The weight of the drone had followed soon after, no less than a hundred pounds landing on top of the two of us.



Grue made a guttural sound.



``On your feet,'' I gasped the words as I tried to haul air back into my lungs.  ``Hurry.''



``We're not unconscious?''  He gave me a hand as we climbed to our feet.



``Spider silk's partially insulated against el-'' I stopped to cough.  ``Electrical charges.''



``\emph{Attention Citizen.}\emph{For your own safety, drop to the ground and place your hands on your head.  You have ten seconds to comply}.''  The broadcasts overlapped, two voices a half-step apart in timing.



I looked up.  Sure enough, there were another two drones in place over me and Grue.



Grue drenched us in darkness, seizing my wrist and hauling me away with enough force that I could barely keep my feet under me.



``Won't work,'' I gasped out the words, ``She's not reliant on conventional senses.  Saw Imp.''



I couldn't hear a response, of course.  I focused my attention on the drones, getting bugs onto them to track their movements, and getting some onto Dragon to see what she was doing.



The drones were falling.  Grue's darkness spread throughout the area, and drones were descending slowly from the air to touch ground.  They weren't discharging their electrical loads either.



Whatever signal Dragon was using to command them, Grue's darkness was cutting it off.



He banished the darkness in a small clearing around us, ``The drones are down.  We could double back, hit her main body.''



I turned my attention to Dragon.  She was rising, planting her claws at the roof's edge, and turning her head to face us.  Her mouth opened.



``Incoming!''  I shouted.  This time it was my turn to grab Grue and pull him away.  We headed for the side of a series of stone stairs.  Crouching so our heads weren't sticking out, we pressed our backs against the side of the stairwell that was closest to Dragon.



The attack was silent, but that was par for the course when Grue's darkness was involved.  It speared down the length of the street like a tightly focused gust of wind.  It scattered Grue's darkness and made the drones skid hundreds of feet along the road's surface.  My hair whipped across the face of my mask in the wake of the attack.



We moved in sync, rushing out of the doorway and rounding the first corner to our right.



With the darkness cleared, the drones were rising again.



``She's prepared for me,'' Grue said.



``Maybe planned to come after you when she was done here,'' I said.  I glanced nervously at the drones that were turning their red eyes to every surface and object, searching for `citizens' to detain.  ``Or it's part of a more complicated setup.  This way.  There's a path through the building and out the other side.''



We were halfway through when a trio of drones moved to cut us off, another drone moving to block our retreat.  It was a precise enough maneuver that I knew Dragon had to have some kind of thermal vision at play, or another means of tracking us.



Grue hit the drones with his darkness, shutting off the connection to Dragon.  We pushed our way past as they settled to the ground.  Dragon was orienting herself for another shot. We had cover, but she had to know that.



The blast of hot wind ripped past us.  The building obstructed the worst of it, but it was less focused than the former.  Again, it stripped away much of Grue's darkness.  He covered them in a fresh layer and we continued running.



Dragon didn't give chase.



\blacksquare



We arrived at Coil's base and I knew from a single glance at Regent's posture that we hadn't all made it.  It was as though we were afraid enough of the answer that we weren't willing to ask; Nobody spoke as Regent and Shatterbird led the way into the underground base.



Imp was just past the last door.  Grue hugged her, and for once she didn't fight or complain.



Coil's soldiers were armed and at the ready, guns resting on knees or from the straps at their shoulders, each man and woman with their specialized body armor strapped on.  Thirty or forty sets of eyes watching us, each of them utterly still.  Coil stood on the walkway opposite us, Trickster to his left, Sundancer and Oliver to his right.



``You made it,'' Tattletale called out.  I'd nearly missed spotting her in the midst of the soldiers.  She was in the company of Fish and Minor, two of the squad captains.



``Who are we missing?'' Grue called out.



``Ballistic, Genesis and Bitch.''



\emph{Damn}.  I didn't particularly like or dislike Genesis, but I didn't want her to suffer.  Ballistic\ldots I couldn't bring myself to care that much.



Bitch, though?  That was bad.



We waited while Coil and the Travelers traveled across the walkway and Tattletale crossed the bottom floor to the staircase.



``This is not ideal,'' Coil spoke.



``No,'' Grue responded.



``Seven of those things,'' Tattletale said.  ``They hit Sundancer, Genesis, Ballistic, me, Bitch and Skitter.  Tried to hit Trickster, but he was recuperating here.  My gut says Dragon's controlling these things with an A.I..  Smart A.I., but they didn't seem quite as sharp as she was in our last run-in with her.  Or her attention's divided too many ways.  Can't say.  Her objective seems to be disrupting our control over the city rather than stopping us outright.''



``I think the pair of us only slipped away because she wasn't expecting me to be there,'' Grue said.  ``Did she use the drone-deployer against you guys?''



``No,'' Tattletale replied.  ``She was piloting an updated version on the thing she used against Leviathan.  Spewed containment foam everywhere.  My guys hammered it with rocket launchers and bought me time to run.  Maybe lost half my squad, depending on how things went.  Only Minor and Brooks have returned so far.''



``Came after me with a bloated floating ship, kept drawing forcefields around me,'' Sundancer said.  She was hugging her arms to her body.  ``My power couldn't even knock them down.  I burned myself an escape route through the ground.  Nearly got trapped in the molten sludge.  It was stupid, I could have died.''



Oliver put a hand on her shoulder.



``Seven different ships,'' Grue said.



``This is well-timed enough that I'd suspect a traitor in our midst,'' Coil spoke, pausing for a moment while his head turned fractionally to take us all in, ``But I haven't spoken of my overall plans to anyone, and there is nobody capable of reading minds to figure out my overall strategy, much less in Brockton Bay.''



``Just bad luck and good planning,'' Tattletale said.  ``Communications are down, no camera feeds, no radio.  Phones too.  No cell or satellite signals are making it out there.''



``So we're going to have to stick together instead of coordinating attacks,'' Grue responded.



``Trouble is,'' Tattletale said, ``They've already laid out their game plan, and it's a toughie.  Seven suits babysitting our territories and keeping us from settling back in.  If we pick a fight like Ballistic did, then they deploy the Protectorate, the Wards and probably any unoccupied suits as reinforcements.''



Nobody had a response to that.  Dealing with just the one Dragon had been hard enough.  Dealing with Dragon plus a contingent of heroes would be next to impossible.



``Can Grue borrow her power?''  Trickster asked.



Grue shook his head, and the darkness around him seemed to expand a fraction.  ``No.  Don't get much from tinkers.''



``Then there's Regent,'' Trickster said.  ``Or, more specifically, Shatterbird.''



``Sure,'' Regent said.



``She might have a countermeasure in mind,'' I said.  ``She knows Shatterbird's here.  It could be as simple as the long ranged wind cannon thing she used to clear away Grue's darkness.  She could shoot Shatterbird out of the air the second she shows herself.  Or any number of things.''



``Try a larger scale detonation?''  Trickster asked.  ``See if you can't wipe out a couple of suits at once, without revealing yourself?''



``No,'' Regent said.  ``Don't know if I can control the area of it if I push out too hard.  It's slippery\ldots I'm not good at explaining this stuff.  I can turn the dial to anywhere from one to ten, but for each number you go up, it goes maybe twice as far, maybe five times as far.  The effect\ldots I dunno.''



``It gets exponentially more powerful, as you put more effort in,'' I suggested.



``Sure.  Don't know what that means, but sure.''



Coil cleared his throat, ``I've invested a great deal of time and money into establishing your two groups here in Brockton Bay, and I did it for precisely this sort of scenario.  Again, the timing is unfortunate, but I still expect you to address this situation.  You'll want to verify whether Bitch, Ballistic and Genesis are captured or simply pinned down somewhere, rescue them if need be and dispatch Dragon.''



\emph{There go my plans with Brian.}



``This may be just a \emph{smidge} above and beyond the call of duty, bossman,'' Regent said.



``You'll have access to all of my resources,'' Coil responded.  ``But the previous orders about clearing out and establishing your territories by noon tomorrow stand.''



``Or?''



Every set of eyes moved to Imp.



``Beg pardon?'' Coil asked.



``Hey, I'm in this for fun, for fame and money.  Getting beat down and arrested isn't any of those things.''



``I see.  I thought you would be more professional.''



``Me?''  Imp shrugged, ``Hell no.''



I could feel the tension in the air.  There were fifty trained soldiers here.  Men and women who could shoot and hit their target.  If Coil gave the order, I wasn't sure we'd walk away in one piece.  Intentionally or not, Imp was pulling the chair out from under Coil at a time when he was already vulnerable and unsteady on his feet.



\emph{Good}.



``Do the rest of you feel this way?''



``The Travelers aren't in a position to walk away.  You know that,'' Trickster said, ``And we have to rescue Genesis and Ballistic if they need it.  So no.  We're definitely in.''



Tattletale, Grue and I exchanged glances.  Tattletale's eyes lingered on me for a long second.  Was it up to me?



``Honestly?'' I said.  ``I don't know what call I'd make.  This is pretty dangerous, as stuff goes, and we didn't exactly sign up for this.  I'd go in just to make sure Bitch comes out of it okay, but doing that \emph{and} cleaning up this mess in the kind of timeframe you're talking about?  That's asking a lot.''



``You'll be adequately compensated for the risk you face,'' Coil said.



``I figured as much.  But I don't want money.''



``Ah.  What \emph{do} you want, Skitter?''



``You know that already.''



``I've already told you I'll consider your request.''



``I want a \emph{promise}.''



He didn't reply.  Instead, he stared at me, his mask opaque, no holes for the eyes, nose or mouth.  I had to read the little details, the movements in the raised portion of his brow, the set of his chin, the movements and tension of his fingers where he had his hands clasped in front of him.  If I had to venture a guess, I'd think he was \emph{offended}.



``Then you have it, Skitter.  Provided you deal with this situation in the next twenty-one hours and your team has reclaimed their territory, I will consider your end of the bargain filled.  I'm hoping I have the rest of the Undersiders as well?''



``I'm not promising anything until I get something too,'' Imp said.



``What would you require?''



``My own territory.''



``That can be arranged.  Given how critical this situation is, are you content to discuss the matter \emph{after} the situation is resolved?''



``Come again?''



``He wants to know if you're okay with deciding what territory you get \emph{after} the job is done,'' Grue said.



``Yeah.''



``Grue, Tattletale, Regent?''



``I'm with her,'' Tattletale jerked a thumb my way.  Grue nodded, glancing at Imp.



``I'm not about to be left out,'' Regent said.  ``But maybe you could pony up a nice cash bonus?''



I could hear the slightest of sighs from Coil.  ``That can be arranged.''



``Cool.''



``Then that's settled.  I've been made aware that Dragon is also making a bid to claim, seize and lock out \emph{digital} goods within the city.  Victor has agreed to work with my teams and do what he can to minimize the damage.  If there's nothing else-``



``There is something,'' Tattletale said.



``Do tell.''



``That data we grabbed from the PRT offices.  You crack it yet?''



``Some.  It's badly degraded.''



``I need it.  As much as you can give.''



``Done,'' Coil said.  ``I can show you the way.''



``One other thing.  You said we had access to all of your resources?''



``Yes.''



``Just how much money are you able to spare?''



``We can discuss that on our way to the room where the databases are stored,'' he said, firm.  ``Undersiders, Travelers, I wish you luck.''



He strode off with Tattletale following.



\emph{Too easy}, I thought.  \emph{He made that promise too easily.}



But it was \emph{something}.



``Let's go,'' I said.





