





``We're not going to be able to take on Dragon without a plan,'' Grue said, ``A \emph{damn} good one.''



``You taking point on this?'' Trickster asked.  He stepped forward to unlock the gate and held it open for us.



I knew Grue well enough that I noticed the delay before he responded. ``I don't have a plan, but I'll take lead if we need it.''



Was he hesitating?  We hadn't really asked a lot of Grue since he'd been taken by the Nine.  Lisa had expressed concerns that he might be shaky if we put him under the pressures a leader had to handle, and the others had apparently agreed.  They'd talked about nominating me.



I wasn't sure I was up for the role, but I was\emph{ }even \emph{less} sure about having Grue calling the shots when he might shut down or get distracted at a crucial moment.  I didn't know what form his trauma might take in this kind of situation.  Our side consisted of Trickster and Sundancer from the Travelers, with Regent, Shatterbird, maybe Victor, Grue, Imp and me. Grue's own self-preservation or his feelings for Imp and me could cause him to play it too safe when we needed to make a decisive strike.



``Actually-'' I started to interject, but the words disappeared the second everyone turned my way.  Grue's attention, in particular, was making it hard to be confident.  I didn't want to hurt him, and trying to figure out how to phrase things without hurting his feelings, raising a sensitive subject and actually saying what I wanted to say\ldots



We'd stepped outside.  The half-finished building that loomed over the entrance to Coil's underground base sheltered us, allowing intermittent sunlight through where plywood hadn't yet been erected to fill the gaps.  Patches of bright and dark.  I turned and looked at Grue, trying to read him, to see if there was some clue about what he'd say.



Regent spoke up, ``Spit it out.  Actually what?''



``Can I?''  I asked.  ``Can I take point here?''



When in doubt, keep it simple.



``You have a plan?'' Trickster asked.



``Maybe.  No, plan is the wrong word.  Call it a strategy.''  I was studying our group, assessing the tools we had at our disposal.  ``But it's becoming a plan as I think about it, and I think Imp plays the key role here.''



``Fuck yeah!''



``\emph{Imp}?'' Trickster asked.  ``Dragon can see her, can't she?  She's the most useless person here.  I mean, I know I'm not in any shape to fight, but at least my power \emph{does} something.''



``Fuck you,'' Imp snarled.



``No,'' I said.  ``We can definitely use her.''



``Let's hear the plan,'' Grue said.  I was relieved that there was no anger or irritation in his voice, nothing to indicate he was upset over my co-opting the leadership role.



``The first priority will be making sure Bitch, Genesis and Ballistic are okay.  I'm thinking the easiest way to do that will be to pay the heroes a visit at the PRT headquarters.''



``Dangerous,'' Grue said.



``And it's something Dragon will anticipate, I think,'' I said.  ``It's a safe bet to say she's smart, even if the actual machines aren't getting her full attention or if they're dumber because their artificial intelligences don't function at the same level as an actual human brain.  She's still organizing the suits, and she's going to be able to anticipate that we might go for the most vulnerable elements of their operation, the local heroes.''



``You're thinking we go after them?''



``We have to.  The individual suits are going to be tough to take down, if not outright impossible.  We \emph{can} take down the local heroes and get leverage, information, or at least stop them from interfering when we go up against one or more of Dragon's suits.''



``Makes sense,'' Trickster said.  ``Unless we're putting ourselves in that worst-case scenario where we're dealing with multiple suits \emph{plus} the local heroes.''



``It's possible.  Even here, I'm willing to bet my left hand that there's going to be a Dragon suit parked on the roof of that building, or somewhere near by.''



``And you're thinking we use Imp?''  Grue asked.



I nodded.  ``We can leave her there as a saboteur, maybe, or just have her in place to get information or methodically take threats out of action.  But it won't be that simple.  They'll have security cameras throughout the building.  Which means we need to take them out if she's going to walk around without a problem.  Regent, can Shatterbird kill all the cameras and lights in the building without killing anyone?  Nothing explosive.''



``A gentle break?  I'd have to be close.  Closer if I don't know where it is.''



``And by `I' you mean Shatterbird?'' Grue asked.



``Yeah.  I can't get that far from her though.''



``I can probably find the location to target with my bugs.  But getting Shatterbird in close means we need a distraction.  So this is a two-pronged plan.''



``The problem with that,'' Grue said, ``Is this is \emph{also} a plan with a lot of steps, each dependent on the success of the step before it, as well as the success of the second `prong'.  If we fuck up or run into a snag somewhere along the line, it falls apart.''



``Yeah,'' I said.  ``And we're going to be outnumbered and outgunned, even if we don't count the squads of PRT uniforms that are going to be stationed in there.\emph{  }But I think we can use that to our advantage.''



``Disguises?'' Sundancer asked.



``No.  Not disguises.  Let's hurry.  We're working with a hard time limit, we have to travel on foot, and we're going to be forced to stay out of the open as we travel.''



\sectionbreak



Grue filled the area with darkness as we approached, and then cleared enough away for us to talk.  With luck, it would help keep them from detecting us with any of the countless tools tinkers like Dragon, Chariot or Kid Win had at their disposal.  Radar, thermal imaging, stuff I'd never even heard of.



They had modified the PRT building since our last visit.  The windows had been destroyed when Shatterbird had attacked the city, and were now filled with screens and plywood.  PRT uniforms stood on the rooftop, observing the surrounding area.  Trucks ringed the area, each with police officers, detectives in bulletproof vests and more PRT uniforms standing nearby.



One of Dragon's suits was perched on the rooftop of the tallest building in the area.  The legs were long enough that the knees rose above the body, ending in four sharp points, and wing panels seemed to join each of the legs, like the flaps of skin between the legs of a flying squirrel.  The actual body was low to the ground, with a long tail that had entwined from a point at the back of the rooftop to the front, caressing the corner closest to me.  The head swiveled slowly from side to side, scanning for threats.



It wasn't the drone ship.  Good.  That would have been disastrous.  But I didn't know what this suit did.  The feature that caught my eye was the wheel.  As big around as the suit was long, the spoked wheel ran through the shoulders of the suit, jutting straight up.  It rotated slowly, arcs of electricity occasionally flashing between the center and the edges, killing any bugs that settled on the spokes and leaving a heavy scent of ozone in their wake.



I described the general shape for them.



``Anyone recognize what Skitter's describing?'' Grue asked.



``That's not the one that came after me,'' Sundancer said.



``It's in my territory,'' Trickster said.  ``Maybe she picked it to come after me?''



``How do you counter a teleporter?''  I asked.



``With that thing, apparently,'' Regent commented.  ``So we're dividing our group?''



``Yeah,'' I said.  ``I'm tracking you guys with my bugs.  Take your time getting into position.  Better to take a bit longer than to alert them too early.  Grue's with me.  Trickster, Imp and Sundancer stay here, keep out of sight at all costs.  Regent and Shatterbird, you stay here in the darkness for cover until we make a move, then head out and circle around.  When we're all in place, I'll let you know.''



Grue and I headed out, navigating through back alleys and side streets, detouring far enough away that the curve of the road kept us out of sight of the officers stationed by the intersection, with my swarm to check for any bystanders and Grue's darkness to keep us off the armored mech's radar.  I used my bugs to start tracking the people inside the headquarters.



Heat and humidity were my allies here.  The main floors had open areas with desks and areas with blocks of cubicles, packed with officers working elbow to elbow.  They'd worked long days, judging by the heavy taste of the sweat on their skin, and they'd let food pile up. With the general warmth of summer, bugs were secretly thriving.  Some vegetable mush had leaked from the trash can to the bottom of a bin, maybe spaghetti or some pizza sauce, and maggots were happily devouring a meal there.  Small flies had amassed where the trash hadn't been promptly cleared away, and piles of paper offered a home to the enterprising spiders that wanted to devour this growing population of pests.



I'd worried I wouldn't be able to get my bugs on everyone present without alerting them.  It wasn't a problem in the end.  A small number of maggots could be delivered by a fly, dropped into the midst of an officer's shoelaces, the pocket of their pants or the holster of their gun.  From there, it was easy enough to keep track of where they were moving and what they were doing.  Counting the bodies, checking the various people inside, I could tell that Bitch, Genesis and Ballistic weren't present.  Nobody matched their build or style of dress, in costume or out.



On the third floor the three local members of the Protectorate were in the company of the Wards, a pair of PRT uniforms and the woman I took to be the Director.  Triumph seemed to be okay, I could sense the general shape of Miss Militia, as well as Assault.  I didn't spot Prism, Cache or Ursa Aurora.  That was good.



All of the Wards were present, too:  Weld, Clockblocker, Flechette, Kid Win, Vista, and Chariot.



We had two big guns.  If we were willing to be monsters, to go all out, it would be a fairly simple matter to hit them with Shatterbird to slow them down, use Sundancer's sun at maximum power, tear the building apart and incinerate the residents before everyone could clear out.  It wouldn't even be hard.



But what was the point if we went that far?  I was in this to save Dinah.  It didn't do any good if I ruined the lives of a hundred Dinahs in the process – the daughters and sisters of the employees here, fathers, mothers and other people who did nothing to get caught up in this war.



``This spot good?'' Grue asked, stopping.



I looked around.  We didn't have a view of the building, but we did have a view of Trickster.  Which is what we needed.



``It's good.  One minute while I fill them in.''



``Feel confident?''



``Wish I had time to practice this before trying it in the field,'' I replied.



``Yeah,'' he answered.



I used my bugs to spell out the various information they needed.  The presence and location of the armored suit, the general number and location of the enemy forces and the floors they were currently on.  It took me a few minutes to spell everything out and verify that they understood.



The plan called for a distraction.  Sundancer would take the lead on that.  I signaled the go-ahead, and she created her orb, shoving it down through the road's surface.  However many thousands of degrees it was, it melted through pavement and bored into whatever pipes and drainage spaces were beneath the roads.



When it rose through an intersection some distance away, it was significantly larger.  Sundancer began bringing it steadily towards the headquarters, moving in towards the opposite face of the building that Grue and I were closest to.



The Protectorate headed to the windows to see what was happening.  I highlighted the window frame with my bugs, clustering them so a general rectangle surrounded the area.  Did Trickster have the ability to see them through the window?  It was hard to calculate the angles-



I found myself in the midst of the local heroes.  Bugs exploded out from within my costume, covering them.  Capsaicin-laced bugs found every uncovered eye, mouth and nose before they realized what had just happened.  My bugs could sense Triumph bending his knees to lunge for me-



And I'd shifted a few feet to the right.  Even as my orientation and senses were thrown by the sudden movement, my bugs let me figure out where I'd moved a fraction of a second before the enemy did.  I was already reaching for my baton, whipping it out to its full length.



Trickster switched me again before I could strike Miss Militia with my combat stick.  Vista was in front of me, and without really thinking about it, I struck her in the most vulnerable area I could reach, across the bridge of her nose, swatting her in the ear with a stroke in the opposite direction.



Another swap, not a half-second later.  We were counting on my swarm-sense giving me the edge in this chaos, the close proximity and unclear positioning of their allies would keep them from hitting me with the worst of their powers.  I caught Miss Militia in the midsection with my baton, swung overhead to try to catch her hand, but missed when Trickster teleported me again.



Assault kicked me before I could recover and strike my next target.  The hit didn't \emph{feel} that hard, but it sent me sliding across the floor, into a trio of chairs with plastic seats.



``The window!'' Miss Militia choked out the orders through the pain of the capsaicin and the massed bugs.  ``Block Trickster!''



I climbed to my feet.  I'd waited too long to signal for an exit.  The plan had been to bring Grue in as I wrapped up my initial attack, let him use his darkness to disable, steal whatever power would serve best and dispatch the enemy.  They'd caught on to what we were doing, and they were making their counter-move.  If Trickster couldn't see me, he couldn't swap me with anyone, meaning I was on my own.



My opponents were suffering, though.  Clockblocker was gone, teleported out as I'd teleported in.  Miss Militia, Vista, Flechette, Triumph, Chariot and Kid Win were down, more or less out of commission with their eyes swollen shut and the bugs crawling into their ears and airways.  At Miss Militia's instruction, they had backed up to the window, blocking Trickster's view.



Besides bringing Grue in, the plan had been for Trickster to swap the heroes out as he spotted them, using bystanders or any officers in the area.  Right this moment, he should have eyes on the uniforms on the roof, could switch their locations with that of the heroes, but he wasn't.  Maybe he felt it was more dangerous for me to be up against a cop with a gun or a PRT uniform with containment foam than against heroes we'd already disabled.



Or maybe he was fucking me over on purpose.  No, it didn't make sense.  He had his teammates to rescue.  I was still suffering latent paranoia from Coil's `test'.



Still, the other heroes were more or less incapacitated.  That left me to deal with Weld, Assault, the two PRT officers and the Director.  She was an obese woman, two-hundred and fifty pounds at a minimum, with an unflattering, old-fashioned haircut that \emph{might} have looked good on a model with the right clothes to go with it.  Neither Weld nor Assault were advancing, choosing to block my access to the exits.  The area was some kind of office, filled with desks, chairs, cubicles and computers.  More like an office building than I'd expected from a law enforcement facility.



``This-'' the Director started, stopping to cough and gag as one of the capsaicin bugs found the inside of her mouth.  It had already smeared its payload along the inside of Vista's nostril, so the payload wouldn't be \emph{that} intense.  ``This was a mistake.''



``If it wasn't a little reckless, Dragon would have probably anticipated it.''



``You've trapped yourself in here.  Two other Dragon models are already on the way.''



\emph{Fuck.}



``Good,'' I told her.  I was pretty sure I managed to hide the fact that I was lying through my teeth.



She straightened, pressing one hand to her right eye.  ``Is this Tattletale's plan?''



``Mine.''



``I see, and-''



I didn't hear the rest.  Behind my back, Assault moved to kick one of the desks.  It went flying into the air in the same instant I threw myself to the ground.  I could feel the rush of wind as it passed over me, hurtling into a cubicle.  I scrambled for cover.



``Prescience.  Interesting,'' the Director called out, as I ducked low and used the cubicles to hide.  ``We assigned you a thinker-one classification, but perhaps we fell short.''



``I \emph{really} don't care.''  I used my bugs to speak, so they couldn't use my voice to pinpoint my location.  She was trying to distract me so the others could act, or buying the Dragon suits time to arrive.  I was calling in more bugs to the area and slowly gathering them around myself, now that I didn't need to worry about people spotting them.



``You can see through their eyes, hear what they hear?  Can you see the suit that was outside?''



The armored mech was moving, its limbs outstretched to catch the air with the flying-squirrel wing flaps.  Panels around its body were venting out hot air and giving it lift, and the giant wheel was tilted back at a forty-five degree angle.  The suit was clearly designed to fly \emph{forward}, relying on the wing flaps to make intricate and acrobatic twists and turns in the air.  Sundancer's miniature sun was blocking the suit's progress, forcing it to make lengthy detours and twist in the air, stalling and dropping several feet before it could catch the air beneath it again.  More than once, it lost more ground than it gained while retreating from the burning orb.



``Yeah.  It's handled,'' I called out, from behind the desk.  My swarm felt the Director make a hand motion, apparently to signal Weld.  As he began advancing towards me, I stayed low and retreated into a cubicle.



The Director spoke, ``More will come.  Not just the seven suits that are currently in Brockton Bay.  So long as you hold this city, Dragon will bring in more suits on a weekly basis.  Dragon will shore up weaknesses, augment strengths.  If you're lucky here, you might win.  I'll credit you that.  But you won't get two or three days of rest before you have to fight again.  How many times can you abandon your territory before your followers abandon \emph{you}?''



The swarm's buzz helped mask the location of my voice.  ``How many times can you afford to let the crooks clean up your messes before the public realizes your Protectorate is little more than good PR, fancy talk and wasted tax dollars?''



``We're doing more than you think,'' she responded.



``And \emph{less} than the people need.  I'm filling a void you people left behind.  If you were doing a satisfactory job, I wouldn't be able to do what I'm doing.''



\emph{Come on, come on}.



``Don't act stupider than you are, Skitter.  The city\emph{ can't} step in to help the people in your territories because we can't trust you.  Your \emph{Bitch} is already mauling anyone that sets foot in her territory.  Any electrician, carpenter or doctor that we send into \emph{your} territory might come back to us dying from anaphylactic shock.''



I shut my mouth.  I didn't have a response to that.  At least, I didn't have a response which wasn't a mere, \emph{I promise I'll be good}.



It wasn't worth worrying about, because I didn't get the chance to reply anyways.  There was a crashing sound and the lights cracked.  Fragments and splinters of glass showered down on top of us as everything suddenly went dark.  To take maximum advantage of this shift in circumstance, I complemented the effect by moving the bugs I'd gathered just outside the windows, blocking the meagre light that was filtering through the screens and plunging the entire room into a dimly lit twilight.



I drew my knife and bolted.  Glass crunched underfoot and caused my feet to slip under me as I ran.  Assault charged my way, one arm still covering his mouth.  More bugs covered the lenses of his mask, but they slid off him as if he were oiled.  His power at work.



With the bugs around me, I pulled a quick, crude decoy together, running in one direction as my bugs moved in another, slightly closer to him.  In the dim, his mask partially covered, he went after the decoy.  When his hand passed through, he reached just a little further to grab a desk and heave it my way.



Once again, I only barely managed to dodge by throwing myself to one side.  My landing was hard, undignified, and ended with the armor of my mask and shoulder hitting the corner where two walls met.



``What are you hoping to accomplish?'' the Director called out.



I stood, trying to look as if I was considering my answer.  Weld was approaching, and Assault stood ready to attack.  Not like he had anything to lose – I was cornered, quite literally.



I turned the knife around in my hand so the blade pointed down and slashed to my right, cutting the bug-covered screen with a loose `x'.  Assault lunged for me, crossing half the room with a single leap.  He was too late – I let myself fall through the third story window.



The outdoors were startlingly bright after the gloom of the building's interior.  I felt my hair whip around me for one second, then landed, sprawling, in a dim setting.



I hadn't fallen the full distance.  I was inside again, surrounded by the other heroes.  I had only a second before they realized what I'd done.  I turned and slashed the screen behind me, throwing myself from the window a second time.



Again, Trickster swapped me with one of the heroes.  I landed with my feet skidding on the floor beneath me and caught the windowsill for balance.  I waved: my signal.



``Get away from the window!''  Assault bellowed.



Then I was teleported yet again.  I found myself back in the alleyway I'd been in with Grue.  Clockblocker was facing away from me, Grue was gone.



A quick check showed he wasn't moving.  Grue had caught him off guard, and his initiative had beat out Clockblocker's concern about potentially disabling an ally.  Clockblocker was frozen by his own borrowed power.  Perfect.



I reached behind my back and unspooled the length of thread.  My bugs took hold of it at various points along its length and began traveling across Clockblocker's body, winding the silk cord around him and tying it in knots.



With luck he wouldn't be a threat even after he got loose.



I reached out with my power to assess the general situation. Grue's darkness surrounded the area, keeping the officers and PRT uniforms at the blockades from opening fire.



The mechanical suit that had been perched on the rooftop nearby was on the ground now, fighting Sundancer, Shatterbird and Grue, the latter two of which were out in the open.



\emph{The plan was to avoid leaving cover}, I thought.



The wheel on the back of Dragon's machine was already spinning at full speed.  I could make out a red eye in the center, identical to the ones that had been on the drone.  The suit thrust itself forward with the vents around its body, lunging for Grue, and Trickster swapped Grue's location with a PRT uniform, putting Grue on the rooftop.  It avoided hitting the man by dragging its two left claws in the pavement, lifting its tail so it wouldn't swing around and strike him.



The wheel blazed with a wreath of electricity, the entire suit thrumming with enough charge to kill every bug touching it.  Without warning, the wheel flared and Grue was yanked over the edge of the rooftop by an invisible force.  Trickster caught Grue, swapping him for the same officer before he was halfway to the ground.



\emph{This is Dragon's counter to a teleporter?}  I would have called it a magnet, but Grue wasn't carrying or wearing anything substantial with metal on it.  Or was this the suit Dragon had deployed against Genesis, Ballistic or Bitch?



Maybe I was missing something.



I used my swarm to keep the windows blocked and the people inside under assault, just enough that they couldn't recover and complicate an already dangerous situation.  I tried to position the bugs I could spare so they hovered around the sensors and the `eye' of the wheel.  Shatterbird was pelting it with a stream of glass shards that looped back in her general direction to rejoin the stream and strike over and over again.



It didn't work.  The thing targeted Grue again and hauled him a hundred feet towards it.  Still crackling with electricity from its nose to the tip of its tail, it advanced on him, tail stretching forward to reach for him.



The machine suddenly shifted position and powered its thrusters to lunge away.  Sundancer's orb erupted from the ground just behind the spot the suit had been standing.  I could see Grue raising his hands to shield his face from the waves of heated air as he scrambled to his feet and ran.



The first of the reinforcements arrived.  I recognized it as the suit that had been deployed against Leviathan.  The same one that had gone after Tattletale, unless she had more than one.  This one had the foam sprayer.  It set down on the edge of the battlefield opposite the wheel-dragon.



\emph{We took too long}.  Or the suits had arrived too soon.  There wasn't really a difference.  The wheel-dragon must have pulled Grue from cover and forced Shatterbird to step up to help, and my own invasion of the main building had taken just a little too long, giving Assault a chance to get his bearings and hit me.



My swarm informed me in advance of the second of the suits that were arriving on scene.  The wheel-dragon thrust itself forward, skimming the road's surface to put itself next to the PRT headquarters.  The drone-deployment suit set down on top of a nearby building so they were spaced out evenly.



They had Grue and Shatterbird surrounded.  I stood off to one side, between the drone-deployer and the foam-sprayer, still too close for comfort but they didn't seem to have noticed me.



I glanced towards the building where Trickster and Sundancer were holed up.  Sundancer wasn't moving her sun, and Trickster was apparently unable to see a valid target to swap Grue for.  The officers and PRT uniforms had been disabled while I was indoors, and both Kid Win and Miss Militia lay at the base of the building.



I used my bugs to write him out an order: `swap me for sun, swap me for kid'.



A long second passed.  Was Trickster illiterate?  Why was it so hard for him to notice the key info I was trying to write down-



I found myself surrounded by darkness.  Only a slit of light filtered into the room through the plywood.  Trickster stood beside me, and the words I'd written out with bugs were on the plywood.  He'd swapped me for Sundancer.



``You sure?''  He asked.  He'd gathered what I was hoping to do.



``Yeah,'' I said.  I pressed my knife into his hand.



He moved me in an instant, putting me at the base of the headquarters, facing a wall.  As I turned around, the three suits shifted position to look my way.



Trickster stepped out of the building, the tip of my knife pressed to the point where Kid Win's chin joined his neck.



We could have used Sundancer's sun to threaten the people inside the building and get the suits to back off, but I didn't trust her to be mean enough.  I didn't have much respect for Trickster as a human being, but that was an advantage when we needed someone to be more vicious.



The suits stood down.  I could see the wheel spin to a stop, the drones returning to dock.



Right.  Dragon wouldn't risk a human life.  She'd discarded her suit rather than let an established \emph{criminal} die.  She wouldn't let a young hero die for the sake of getting us into custody.



``Let's go!'' Trickster called.



I hurried to cross the area between the three Dragon-suits, Grue joining me halfway.  Trickster backed up with a barely conscious Kid Win in his grip.



We'd nearly reached safety when one suit shuddered to life.  Trickster spun around, still holding Kid Win, turning his attention to the wheel-dragon.  The wheel was moving again. ``No funny business!''



It wasn't the wheel-dragon that attacked.  Before I could open my mouth to warn Trickster, the suit with the containment foam sprayed him, swamping him from behind.  The weight and force of the spray knocked his knife-hand away from Kid Win, and the swelling, gummy mess kept it away.  The sprayer proceeded to slowly bury the two of them, trapping hostage and hostage-taker together.



``Swap for Miss Militia!''  Grue shouted, turning around as the drones began deploying once again.  The wheel was getting up to speed, crackling with electricity.



``Can't- Can't turn my head to get a look at her!''  The foam was spraying him from behind.  If he turned his head, he'd be blinded.



And we weren't in a position to grab her and haul her into Trickster's field of view.  It would take too long.  Drones were sweeping down onto the street level, moving into position so they hovered above Grue and I.  I waited for the electrical charge to hit.



It didn't.



The drone tapped my head as it descended.  I stepped back and let it descend slowly to the ground.



The foam sprayer had stopped.  Trickster was buried up to his waist, Kid Win face down in the foam in front of him.  The wheel was spinning down for the second time in the span of twenty seconds.



Trickster swapped himself for Kid Win, putting himself knee-deep in the foam.  He craned his head around and managed to get Miss Militia in his sight, then swapped for her.



We ran, following after the others, who'd already left the battlefield.



``Why did they stop?'' Grue asked.



I shook my head.  ``Tattletale?''



I kept waiting for the suits to perk up and give chase, or for further reinforcements to appear.  There was no pursuit.  Fifteen minutes passed before we had to stop, settling in an abandoned building to hide and catch our breath.



I sorted out my weapons, taking my knife back from Trickster, and sat down to rest.  I ran my fingers through my hair to get it in a semblance of order.



My fingers snagged on something.  For a second, I thought maybe I'd gotten some containment foam in it.



No.  My hair was tied around a piece of paper.  I had to use my bugs to untie it.



I recognized the lettering.  A series of symbols that all strung together so it was hard to tell where one began and one ended.  I'd designed it, when I was making up the code to keep my superhero notes private.



I'd left myself a message?  When?



``I gave myself a reminder, telling me to take our group to the south end of the main beach,'' I said.



``The fuck?'' Regent asked.



``I dunno,'' I said.  ``But we didn't get the hostage we'd planned on taking, so I think we should go, if nobody else has a better idea.''



\sectionbreak



It took some time to get there, sticking to back alleys and roads, and it took more time to verify that there were no threats in the area.



As confusing as the message was, everything made sense when Imp made her presence known, dropping the veil of her power's effect.



Right.  I'd had her tie the note into my hair so it wouldn't confuse or distract me while I was in the field, something I'd only notice after the fact.



She was practically bouncing with excitement.



``Saved your asses,'' she said.



``And she's never going to let us forget,'' Regent commented.



``You got out okay?'' Grue asked.



``I marched the fatty out of the building as soon as I'd made sure the robots weren't going to attack again.  Grabbed the keys from a cop and drove off.  No way you can say I'm useless again, Tricksy.''



Trickster looked at her `guest'.  ``I won't.''



Director Piggot, the fat woman, was handcuffed and kneeling beside Imp, head hanging.



``Well,'' I said, ``Could have gone better, but we got what we needed.  You had her order them to shut down, right?''



``Yup.''



``Dragon must have given the Director the ability to command the suits.  Wouldn't have guessed,'' Grue said.



I nodded in agreement.  ``It's a matter of time before they arrange some workaround, take away the Director's access or Dragon reprograms the suits, but this is good.  We've got some leverage now.''



The Director raised her head to direct a glare at us with swollen, bloodshot eyes.



Funny as it was, I couldn't bring myself to feel bad about it.





