





Well, we'd gone up against Dragon, the Wards and the Protectorate at the same time, and our pains had earned us our hostage.  I was worried the next part would be harder.



Trickster started fishing through the pockets of the Director's suit-jacket.



``Looking for this?'' Imp held up the Director's phone.



``Yeah,'' Trickster replied.  He took the phone.  ``There's a chance it's not scrambled.''



``Bad idea,'' I said.  ``If-''



I stopped when Grue reached over and blanketed the Director's head in darkness.



``Don't need her listening in if we're talking strategy,'' Grue explained.  ``Go on.''



``If Dragon's listening in on the call, and it sounded like she was, we might accidentally divulge some crucial info.  Or we could be alerting those suits to our location.  Or the location of whoever you're calling.''  I finished.



``Might be.'' Trickster replied, ``But it's handy to be able to contact others, and that might be worth the chance that we'd have to run again.''



``Maybe.''



Trickster went on, ``We could call Tattletale right now, hop in the truck Imp brought and have her meet us somewhere secluded, \emph{or} we could split up, with one or more people going ahead to pass word on to her, then wait for her to meet us, wasting a hell of a lot of time in the process.  Keep in mind the suits are still disabled.''



``There's still the Protectorate and the Wards,'' Grue said.



``The only ones capable of moving that fast are Assault and maybe Chariot,'' I said.



``We're short enough on time, and we need to know what happened to our other teammates,'' Trickster said.



``It's not a good idea.''  Grue folded his arms.



``I'm making the call anyways.  We can't afford to wait.''



Grue stood there, literally fuming as the darkness roiled around him.  After a few long seconds, his pose relaxed and he held his hand out, ``Then let me talk to her.  We have a password system.  The rest of you, keep an eye on \emph{her}, and don't forget to watch out for incoming threats.''



``Good man.  The two of us will be over there,'' Trickster said, pointing to one area where sand and debris had been bulldozed into a small hill.  ``Need to talk with `Dancer for a second.  Shout if you need a hand.''



I nodded.  Grue, Trickster and Sundancer all stepped away, leaving Regent, Shatterbird, Imp and I to watch over our hostage.



A minute passed, and she shifted position, her head leaving Grue's darkness.



``Back up,'' Regent warned.



``I have bad knees,'' the Director said.  ``I will if you make me, but it's painful.  I suppose that could be a way of easing into torture, if that's your style.''



``Sounds like a plan,'' Regent said, uncharacteristically cheery.



``No,'' I told him.  To her, I said, ``Sit however you want.  We'll cover you again if we start talking work.''



She gave me a curt nod.



``Maybe we should get her to command the suits?''  Regent asked.



``Won't work,'' the Director replied.



``Why's that?''  Regent asked.



``I can send them in, I can tell them where to go or when to stand by, but they do what they're programmed to, and they're programmed to avoid attacking civilians and local heroes.''



``That didn't stop the foam-spraying-''  Regent started.



``The Cawthorne model,'' the Director interrupted.



``Sure.  That didn't stop the Cawthorne thing from shooting Trickster when he had Kid Win hostage.''



``I expect Dragon accounted for the fact that you might take hostages and use the nonlethality restrictions of the A.I. against it.  She would have given the machines tools or strategies to work around it.''



``And you're just volunteering this information?'' I asked.



``I said it earlier, I think, but you're not a stupid girl, Skitter.  Reckless, shortsighted, capricious, violent, even vicious\ldots but not stupid.  I'm hoping you have the sense to realize how dangerous your current position is.  There will be more mechanical suits coming.  There \emph{will} be heroes coming to Brockton Bay to assist us.  You can't afford to hold this city, and we can't afford to let you.  Not in the grand scheme of things.''



``She likes to jabber,'' Imp said.  ``Should we gag her?  Or make her stick her head back in the dark?''



``Might be better,'' Regent answered, looking down at the Director.



``Need a cloth.  I could pull off a sock, jam in her mouth, maybe we tie it in there with Skitter's silk.  My feet are sweating like crazy in these boots, so it'd be really gross.''



``No,'' I said.  ``We're not going to humiliate her.  We get the information we need from her, see if we can't use her as a hostage to leverage for peace.  That's all.''



The Director shook her head.



``What?''



``Extorting for peace when you started the war.''



``When are you saying we started the war?  When the ABB came after us and we fought back?  When we ambushed the fundraiser to embarrass you?  When we fought Leviathan and the Slaughterhouse Nine and then picked up the pieces ourselves, clearing our territories of the low-level threats while leaving the civilians more or less alone?''



``Except for Bitch.''



``We adjusted Bitch's territory so she wouldn't have as much cause to harass the locals, not so long ago.''



``I suppose that's a consolation to the people she injured.''



``I'm not saying we're perfect.  We aren't.  But we're doing \emph{something.}''



``So are we.''



``You're not doing enough.''



``And when you subtract the blood you've spilled and the pain you've caused, have you really done that much more, Skitter?  That's oversimplifying, obviously.  Right and wrong aren't a matter of adding the good deeds and subtracting the bad.''



``I'm bad at math anyways,'' Regent said.



The Director ignored him, her eyes on me.  ``I presume you've been paying for the supplies and materials you've been importing to your territory with your own money?  You've been paying your people, I know.''



``Yeah.''



``How much damage was done in the course of earning that money?  I see the repercussions you don't.  Things pass my desk: hospital bills, property damage, psychiatrist's notes.  People lose their jobs, lose precious belongings.  Parents are woken in the middle of the night because their children are seriously injured.   I see the details from detectives in narcotics who track the drug trade-''



``I-''



She interrupted me before I could protest.  ``I know you don't sell drugs, Skitter.  But you're interacting with people who do.  If you buy a favor from someone who does, the Merchants, Coil, the Chosen, then you're indirectly supporting that trade.  Just like you're supporting any number of evils every time you help a fellow villain.  I've talked to homicide detectives who have dealt with the bodies in the wake of your shenanigans.''



``We don't kill.''



``People die when you start feuds.  Bakuda was injured by you in one altercation, and she attacked the city over the course of several days.  Do you know how many people were harmed, then?  Because you set her off?  I could show you photos.  People with flesh melted off, frozen, burned, turned to glass.  When I don't see these things in person, I see them on my desk, in high-definition glossy photos.  I could arrange for you to see the photos if you don't believe me, or if you want to see the damage you've done for yourself.''



``No.  I don't need to see them.''



She looked up at me, one eye half closed, both eyes bloodshot.  ``Why is that, Skitter?  Are you afraid facing that reality would shatter this nice little delusion you're living under?''



``I'm not to blame for whatever crimes Bakuda committed.''



``You played a role.''



``Anything she did is on her head, just like anything the Nine did is on \emph{them}.''



``Where do you draw the line?  When do you start taking responsibility?  Or will you explain away every evil you've done and count only the actions you want?''



I could have protested, argued that I \emph{did} take the blame for some things, I \emph{did} blame myself for Dinah, for not seeing the bigger picture, for acting when I'd known Coil needed a distraction for something bigger.



``Hey,'' Regent said.



I turned to face him.



``This is going nowhere.  Let's wait until Tattletale can talk to her.''



``Right,'' I said.  Not only had it been going nowhere, but she'd had had the upper hand, so to speak.  Not necessarily in the strength or validity of her arguments, but in the psychological and emotional sense.  I'd failed to budge her and she'd provoked a response from me.



The Director didn't open her mouth again, apparently satisfied.



Grue returned with Trickster and Sundancer following behind him.  ``Imp, where's the truck you used to get here?''



``You passed it as you came here.''



``We'll have to be careful,'' Grue said,  ``Anything from the Protectorate, \emph{her} included, may be bugged.  No talking about anything sensitive on our way back, and we'll ditch it asap.''



We nodded.  I had only the one good arm, my other shoulder still tender, so I walked around to the Director's left side to grab her under the shoulder and help haul her to her feet.



I was surprised that she cooperated.  If she'd delayed us by forcing us to carry her, she might have bought time for reinforcements to arrive.  If we'd forced the issue with violence, it would have reinforced her argument.



In her shoes, I might have done it, just to apply that stress to my enemy.  It said something that she didn't.  I just wasn't sure what.



\blacksquare



We emerged from the truck at the rear of a liquor store.  Tattletale stood in the open doorway of the loading area with Brooks and Minor beside her.



We hauled the Director out of the back of the truck.  Grue had covered her in darkness to keep her unawares, and she looked more than a little disoriented.  Her hair was in disarray and she couldn't fix it with the cuffs on, and the effects of the capsaicin hadn't entirely worn off; her eyes were puffy, her face red.



But when she looked at Tattletale, the smallest smile touched her lips.



``What's this, Piggot?'' Tattletale asked, hopping down from the ledge to the parking lot.  ``Looking forward to a duel of wits?''



Director Piggot shook her head, still smiling.



``Staying mum?  Lips sealed, so you can't betray vital information?''



``I trust you'll get it anyways,'' the Director replied.



``First things first,'' Grue said, ``Are we bugged?''



``The truck is.  But we'll have my guy drive it a ways and then leave it somewhere.''  Tattletale jerked a thumb towards Minor, and he marched over to the truck, catching the keys as Grue tossed them.



``They'll know the truck stopped here,'' the Director said.



``I know.  We're going to go for a walk,'' Tattletale said.  ``Up for that?''



``I don't think I have a choice, do I?''



``Nope.''



We headed down a back alley.  I saw the Director struggling to keep her feet under her, her pumps sloshing in shallow water.  She stumbled once, and I put a hand out to steady her.  I was more likely to be crushed beneath her than to catch her if she fell, but at the same time, I wasn't sure we could get her off the ground without uncuffing her if she did slip.



I didn't like her.  Maybe that was an obvious conclusion for me to come to, but she reminded me of my high school principal in some ways: she was the authority figure, the person who embodied an institution I had no respect for.  On a more concrete level, she was indirectly or directly responsible for Armsmaster, for Sophia and the other bullies getting away with what they did.



Even on a basic, abstract level, she reminded me of Emma in how quickly and easily she'd gone for the throat in trying to cut me down and provoke a reaction from me.  Again, much like Emma, it was all the more nettling because she wasn't entirely wrong.



``You have our teammates in custody?'' Tattletale asked.



The Director didn't respond.



``That's a no.  Which means they're either injured or dead and you aren't aware, or they're holed up and can't leave their territory because of the suits that are sitting there.''



``Perhaps.''  Even with the unsteady footing, the Director was focusing more on Tattletale than where she was going, studying her.  But I knew that if \emph{I} could see that much, Tattletale would as well.



``Is Dragon in town?''



``Last I saw,'' the Director replied, hedging.



``She's gone,'' Tattletale said, for the benefit of the rest of us.  ``Another task.  Wouldn't be an Endbringer.  Not yet.  The Nine.''



``Yes.''



``Want to give up the information now, spare me the hassle of twenty questions?''



``My delaying you means the other models have a chance to find and arrest your teammates.  You'll have to ask.''



``We have other tools at our disposal,'' Tattletale glanced at Regent.



``And \emph{I} know Regent takes anywhere from fifteen minutes to two and a half hours to take control.''



``After which point you wouldn't ever be able to work in this town again.''



``Taking the same approach you did with Shadow Stalker?''  The Director asked.



I raised an eyebrow.



``Yeah, like Shadow Stalker,'' Tattletale replied.



``We have records from when Regent worked for Heartbreaker, under his previous name, Hijack.  Interviews with people Regent controlled.''



``Good for you,'' Regent replied.



``I know his power gets weaker as you spread it thin, control slips.  You can't afford to loosen your hold on Shatterbird, so no, I don't think you'll try to take control of me.''



``And you believe that,'' Tattletale said.  ``Enough that you're confident.  You aren't worried here, even when you've been taken hostage.''



``Which leaves you the options of playing twenty questions to get all the information you need, or you can try something more dire.  Torture?''



``That's the second time she's brought that up,'' I said.



``Because she's trying to get a sense of us,'' Tattletale said.  ``She wants to see our reactions and body language as the subject comes up.''



``Yes,'' the Director said.  ``Based on that much, I'm almost certain you wouldn't torture me and you aren't the type to kill unless absolutely backed against the wall.  Which means I can be home before midnight.''



``A little optimistic,'' Trickster growled the words.



``I don't think so,'' Director Piggot replied, turning to level a glare at him.  She looked almost feral, even as her voice was controlled.  ``See, I know \emph{you }might try to kill me if these others weren't around.  But the others won't let you.  There's Regent too: little to no compunctions, as we saw with Shadow Stalker.''



Her eye darted to Tattletale, then to Grue, and finally to me.



``Do they know the full story?'' the Director asked.



``No,'' Tattletale replied.  She sighed a little.



``Tell us what?'' I asked.



``I'm interested, too,'' Grue added.



The Director only smiled.



``Do you trust me?''  Lisa asked.



``Pretty much,'' I replied.  ``A little bit less right now than I did a minute ago.''



``Fair.  She's trying to derail our interrogation.  She knows we won't get violent with her to get the details we need, but I'll be able to get the answers out of her with a bit of time to ask and apply my power.  Knowing this, she's trying to fuck with us, set us against each other, and delay us.''



I nodded slowly, glancing between Tattletale and Director Piggot.



Tattletale shrugged, ``If you trust me, can you agree to drop the subject?  I'll explain before too long.''



``Knowing is half the battle,'' the Director said.  ``Only half.  Being aware of what I'm doing doesn't stop me.  I've learned a lot since you took me hostage, and I already knew some things from research, observation, paperwork and background checks.  I have a read on your personalities and how you operate, and I know some background details.  How is your brother, Tattletale? \emph{Sarah}?''



\emph{Sarah?}



I glanced at Tattletale, saw a flicker of emotion cross her face before she smirked, wagged a finger at the Director and spoke with a touch too much cheer, ``Low blow.''



``I've been looking forward to having a conversation with you for some time, playing it out in my head.  I paid out of my own pocket for information so I can beat you at your own game.  You would have done well to erase the trail leading back home, \emph{Sarah}.  But then, that would have required thinking about it, maybe even going back.''



``You're \emph{glad} we took you hostage.''



Piggot smiled.  It wasn't pretty.



``Ball's still in our court,'' Tattletale said.



``But you have a time limit.  Like I said, I expect to be home and in my bed before the night's out.''



``You have a card up your sleeve, leverage.''



``In a way.  I'm dying.''



Our group had been walking across a street, and we all stopped to look at her.



``You need constant medical care?'' Tattletale said.



``I have a setup at home.  Hemodialysis.  I hook myself up to it every night, flush my blood of excess water and pollutants over the course of eight hours while I'm sleeping.  If I don't get the dialysis, I expect I'll go downhill very quickly.  My body's already in rough shape, and I've overworked myself these past few weeks.  I wouldn't die that quickly, but you wouldn't get any use out of me, either.  So we get to enjoy each other's company for about five or six hours.  Then you decide whether you let me go home or whether you let me die.''



``And in the meantime, you intend to stall.''



``To the best of my ability,'' the Director said.



``What suit did they send against Bitch?  Hellhound?''



``Did you know your parents are still looking for you?  They never stopped.''



Tattletale pursed her lips.  ``A model Dragon's used before?''



``You should have seen the looks on their faces when I told them you were alive and well,'' Piggot said.  She measured the look on Tattletale's face, smiled.  ``Yes, I visited them in person.''



Tattletale's eyes narrowed.  ``I could turn the tables on you, pick \emph{you} apart.''



``Please do.  Waste time.  You won't accomplish much.  \emph{Look at me}.  You know as well as I do that I wear my shame and disappointment on the outside, for the world to see.  I had the muscles of my legs torn apart years ago on the job, lost the ability to keep up exercise, coupled with hours behind a desk, hours of the dialysis and recovery from surgeries, no time to take care of myself with work.  I know I'm ugly, I know I'm fat.  There's nothing you could say to me that I haven't said to myself a hundred times over.''



``You sound almost proud,'' Trickster said, a hint of disgust in his voice.



``I have no powers, Trickster.  I'm lowly, a mere mortal compared to you.  I admit it, I \emph{admit} I'm weaker, slower, my options are pretty limited in a fight.  But I'm \emph{tenacious}.  I'm shameless, if I have to be, because I \emph{refuse} to lose to you.''  Her voice bordered on a growl as she uttered the word `refuse'.



\emph{This} was the director of the PRT?  Hearing her speak, I'd almost thought she was like Coil, at first.  Cultured, proud, arrogant.  Now that she was showing her true colors, it was almost the opposite.  And strangely, it was equally problematic.



A fleck of spit flew from her lips as she continued her rant, ``And I find it pretty \emph{fucking} poetic that I have the upper hand because of the very things that you capes look down on us for.  I'm fat, frail, scarred, and I have old wounds that I'll never recover from.  But because of that, because I could die in a matter of hours if you don't let me seek treatment, you're either going to have to compromise with your personal code or you're going to have to let me walk away and find \emph{another} way to beat Dragon.''



\emph{This isn't working}.



``Trickster, watch her,'' I said.  ``Sundancer, you and the medic watch Trickster \emph{and }the Director.  Rest of you with me.  We'll talk over there.''



We retreated from the woman.



Regent ran his fingers through his hair.  Tattletale had her arms folded as she leaned against a wall, staring at the ground.  She wasn't smiling, and she wasn't venturing to comment.



``What're you thinking?'' I asked.



``This isn't working, obviously.''



``We could take her to her house, give her the treatment she needs,'' Grue said.



``That's what she wants.  There's a trap there.  Either she's got some measures in place at home, guns hidden where she can get at them or some kind of safe room, or the PRT is already there, waiting to ambush us.''



``I could control her,'' Regent said.  ``Send Shatterbird back, lock her up, get control.''



``Which would take time, again,'' Tattletale said.  ``The benefits would be negligible, and it would take longer than you think, because she's trained in resisting mental and emotional attacks.''



``I wouldn't have thought,'' I commented.



Tattletale shook her head, ``Let's figure it's half an hour for Shatterbird to get snug in her cage.  Two or three hours to get control of her\ldots and for what?  They have an idea we captured her.  If they haven't revoked her access and powers by now, they will have by the time Regent's finished with her.  So how do we use her?''



``We're running out of time,'' Grue said.  ``It's maybe two or three in the afternoon.  That gives us maybe twenty hours to get this done by Coil's schedule.  Brainstorm.  More ideas, come on.''



``We could abandon the job.  Say fuck you to Coil, let his grand plan fall apart,'' Regent said.  ``Get Bitch and leave town.''



``I don't like that,'' Grue said.  ``On a lot of levels.''



``Sure, sure.  But it's the most obvious choice.''



``Not an option as far as I'm concerned,'' I replied.  ``I won't blame you guys if you want to do that, but I gotta do this, finish the job or fail trying.''



``Okay, I sort of expected you to say that.  Um, hear me out on this before jumping down my throat, but why \emph{don't} we torture her?  She's been begging for it, practically.''



I stared at him.



``Torture doesn't work,'' Grue said\emph{.}



``Without getting into too much detail, I'd say it does.  Sometimes,'' Regent replied.



``Not with someone like her,'' Tattletale said, sighing.  ``Even if she didn't have a background in that sort of thing, her personality\ldots if anything I think she'd be \emph{glad} we did it.  Not while we were doing it, but it'd validate her view of the world.''



``Which is?'' Grue asked.



``That we're monsters.  In her eyes, our trigger events highlight a moment at the worst point of our lives and our powers make it so we can never put that behind us.  Good guy or bad, she sees us as walking personifications of whatever issues drove us to get our powers in the first place, inflicting some shadow or abstract representation of those traumas on others with our powers.''



``How can someone educated and professional like her think that way?''  Grue asked.



``For one thing, she's not all that wrong,'' Tattletale replied, shrugging.



``Hm?''



``We are.  But even people without powers are walking issues.  That's no big surprise.  Having powers just\ldots makes it all more noticeable.  Piggot's suffering from some tunnel vision, is all.  Happens with any bigot.  \emph{Anyways}, my point was, if we torture her, we're only reinforcing her worldview.  It would almost negate any psychological stress we put her under.  No, torture is out for a few reasons.''



``What if we give her treatment?''  I asked.  ``Not at her house.  Off-site.''



``We'd be showing our hand, maybe cluing her in to our connection with Coil, and it would still take time we don't have,'' Grue answered.  ``Nothing saying we'd get enough in the way of answers to be worth the time spent.''



``I don't see what was wrong with my suggestion,'' Imp said.



``Which was?''



Imp pulled off her boot and then peeled off a knee-high sock, wiggled her toes before jamming her bare foot back in the boot.  She stretched out the sock, ``Gag the fatty.''



``I need her to answer if I'm going to get the detail we need in any reasonable length of time,'' Tattletale said.



``She's not answering anyways, right?  Get what you need from her body language.''



Tattletale frowned.  ``Yeah.  You're right.  But it's going to take time.''



``And we're operating in the dark until then,'' Grue said.



``We did okay with the last fight,'' Imp said.



``Barely,'' I cut in, at the same moment Grue said, ``We didn't-``



``We walked away,'' Imp clarified.



``Where are you on the other thing, what you were talking to Coil about?''  I asked Tattletale.



``Trying to get info.  It's hard with the way communications are down.  We sent some soldiers out in trucks, each going down a different major road in the hopes of getting far enough away to get cell service.  Then they gotta get \emph{back here }to bring me what they got.''



``Time's our most valuable resource here,'' Grue said.



I spoke up, ``I don't think we can afford to wait until we hear from your soldiers or the Director.''



``Heading out?''



I nodded, pointing towards the others.  We rejoined Trickster, Sundancer and Brooks.  Imp shoved her sock in the Director's mouth and took the silk cord I offered, tying it in place.



``Careful,'' I said.  ``Trouble with this sort of gag is that if she pukes, she could choke on her own vomit.''



``How do you know these things?'' Regent asked.



``I'll be careful,'' Tattletale assured me.



``Let's plan, then.  Tattletale, any idea if the other suits would be active yet?  The ones we had Piggot shut down?''



``Not yet, but soon.''



``Then I'm thinking we should split up into two teams'' I said.  ``Strike while the other three suits are shut down and waiting for Dragon's attention.  If we can rescue our teammates, we'll be half-again as strong.''



``We don't have the firepower to fight those things,'' Trickster said.



``We have lots of firepower,'' I replied.  ``Problem is they have a lot \emph{more}.  So pick your fights, strike at the right time and hit hard.  Play dirty, don't give them a chance if you can help it.  Grue, you should go with Sundancer and Trickster, so we've got even numbers on both sides.''



``You sure?''



``Your power works well with Sundancer, keeps the enemy unaware until she can get that miniature sun close, and you can keep them off the machine's radar, thermals or whatever.  Hopefully.''



``And you?''



``My bugs will give us early warning if a suit's nearby, and they might alert me if there's radar or anything subsonic.  If Regent and Imp come with me, we'll have some firepower from Shatterbird.''



``Okay.''



``My team will go see if we can find Bitch, rescue her from whatever they sent after her.  You guys do what you can to rescue Ballistic, then hunker down.  If you succeed, stay put, wait for us.  If we don't arrive before dark, assume we lost, mount a rescue.  If you aren't there, we'll assume the same.''



``Sounds good,'' Grue said.



``Either way, we'll figure out where we're going from there.''



The Director raised her head, staring up at the sky.



``You have something you want to say?''  Tattletale asked.



The Director shrugged.



Tattletale removed the gag.  ``What?''



``I'm looking forward to this.''



``Which part?''  Tattletale asked.  ``The interrogation?  The rescue mission?''



``The fight.  Seven suits in this city right now.  The Melusine-six, Cawthorne M.K. Three, the Glaurung Zero, the Ladon-two, the Astaroth-Nidhug, the Pythios-two.  That's six ships right there, that Dragon explained were old models.  Previous versions of her suits that were cannibalized for parts, abandoned after taking severe damage and recently repaired or simply outdated.''



``And the seventh?''



``The Azazel.  Note that there's no version number.  It's a fresh design, crafted to go up against the Nine and put up a serious fight.  The first truly original suit she's made in four years, and I assure you that Dragon has advanced her skills in that timeframe.  If that isn't enough of a pedigree, the Azazel was created by Dragon working in tandem with her new partner, a fellow tinker.''



\emph{Armsmaster.}



She saw the reaction from us, smiled a little.



``Yes.  A new partner.  It was \emph{his} suggestion that we park the suits here when they aren't needed.  And even though I know he's a new cape, nobody you'd know, \emph{certainly} nobody who'd have a grudge,'' she smirked a little, ``I think it's a safe bet to say he had you in mind when he was building it.''



Tattletale jammed the sock into Piggot's mouth and turned to us.  ``Which ones did you fight?''



``Foam sprayer, drone deployer, forcefield generator and a wheel-dragon with electricity and some electromagnet,'' I said.



``Cawthorne, Glaurung, Ladon, Pythios, I'd guess, with only the names and what little I've seen of Dragon to go by.  That leaves the Astaroth-Nidhug, Melusine and the Azazel.  One went after Ballistic, another after Genesis, and a third went after Bitch.''



``Meaning that with the way we're splitting up and taking on whatever machines attacked our missing teammates, each of our groups has a one-in-three chance of going up against this Azazel,'' I concluded.



``Better cross your fingers,'' Tattletale suggested.





