





I was turning to leave when I was struck with a thought.  ``Did Bitch move to her new territory yet?  I know we planned for her to relocate to the city outskirts.''



``Not yet,'' Tattletale answered.  She was tying the gag back in place.  Piggot was screwing her eyes closed in disgust.



``So she's somewhere near the Trainyard.''



``Yeah,'' Tattletale replied.



``We're going to need transportation if we're going to get there without losing too much time.''



``Brooks can hotwire a car for you, show you how to start it up again when you're ready to head back,'' Tattletale suggested.



``No.  I'm not sure it'll be able to navigate all the fenced off areas and debris that'll be in the Trainyard.  Bitch hasn't been clearing the mess, as far as I know, and it wasn't easy to navigate to begin with.''



``If we use the car to get there\ldots'' Grue started.



I finished his sentence for him, ``We run the risk that it'll break down, run out of gas or get wrecked somewhere, stranding us and forcing us to hike across half the city to get to Ballistic's territory.  Let's minimize the opportunities for stuff to go wrong.''



``Beggars can't be choosers,'' Tattletale said.



I glanced at Piggot.  ``We're \emph{capes}, not beggars.  I was thinking about Sundancer and something like a hot air balloon, but I'm not sure how much forward acceleration you could pick up that way.  But something like that.  A lot of our powers operate off virtually limitless power sources.  I've used my power all day, every day and I haven't been any worse for wear.  Can we use that for some extra mobility while we don't have Bitch on the team?''



``You could try a James and the Giant Peach thing with us,'' Imp said, ``Only it'd be backwards: bugs on strings and the `bird along for the ride.''



I shook my head.  ``My bugs \emph{would} get tired.  That leaves Shatterbird.''



``I can only fly with one person, \emph{maybe} two,'' Regent and Shatterbird spoke in unison.



``What if you aren't flying?''  I asked.



\blacksquare



Maybe not my best idea in retrospect.



We were putting our lives in Shatterbird's hands.  Or in Regent's hands, depending on how I interpreted it.  Which wasn't to say we weren't getting where we needed to be in record time.



Shatterbird had pressed and embedded glass into the wood of a door we'd taken off the hinges, and Regent, Imp and I were standing on the surface while Shatterbird flew above us, using her power to pull on the glass.  With our weight resting more towards the back than the front, the door was angled upward, skimming on the surface of the road or through the shallow water of streets that were still flooded.



We had to be pushing forty or fifty miles an hour, and any time we were forced to make a turn, we inevitably went wide, sometimes bouncing off of a wall.  That was without getting into the cars and debris that still covered the roads or our total lack of solid hand-holds, seats, seatbelts or brakes.  I'd parceled out silk cord to grip, but they also served to emphasize how momentum swung us out to one side or another when we turned.  It was easy to underestimate how fast even a lower cruising speed was when safe inside the interior of a vehicle, removed from the road by two to four feet of solid material..



Either way, we headed into the thick of the Docks.  Our makeshift vehicle sped towards a chain link fence.



``Regent, fence,'' I warned, leaning forward to speak into his ear and make sure he could hear me.



We continued forward without slowing.  Half a block away, seventy feet away\ldots



``Fence!'' I raised my voice.



Thirty feet away\ldots



Shatterbird hit the fence with a wave of glass, knocking it down to a forty-five degree angle.  Our makeshift craft lifted up fractionally and we hit the makeshift ramp, remaining airborne for only a second or two before hitting the ground and continuing forward.



``You \emph{dick},'' I swore.



Regent and Imp laughed and cackled.



What had I been thinking, inflicting this pair on myself?



We made our way into the Trainyard, and the ride became much bumpier as we navigated areas with overgrown grass, train tracks and piles of trash.  A crash and howl informed us of our destination before my bugs did.  I signaled Regent when we were close enough so he could bring the craft to a stop.



Bitch and the dogs were fighting, and there were signs the fighting had been going on for a while.



There were six dogs in the area, including Bastard, Bentley and Sirius, but only Bastard and Bentley were still fighting.  Bitch, Barker and Biter had stepped up to fight, as well, with Bitch's civilian henchpersons were hiding nearby.  The vet-girl was taking care of a smaller dog.



Looking at the situation, I couldn't figure out why they'd be having trouble with their opponent.  Dragon's suit wasn't that large, didn't seem to have that much in the way of weapons or gear.  She stood maybe eight feet tall, eight feet wide, with each arm forming roughly a third of its mass, ending in disproportionately large, squat claws.



Barker screamed, then slammed his teeth together with a clack my bugs could hear.  His power turned the noise into a concussive force, erupting around the armored suit.  The suit reeled, staggering back from where it stood on top of a derelict train, nearly falling.  One of the dogs charged and tackled it, tearing into it with claws and teeth.



The suit hauled the dog off it, climbing to its feet in an instant.  It leaped forward to close the distance to its human opponents, and Biter stepped forward to meet it, his fist swelling to five times the normal size, along with the spikes and blades he'd worked into the fabric of his glove.  The suit went flying, gathering itself into a rough ball shape as it careened backwards into the side of a train.



Had we stepped in just as the fight was wrapping up?



The suit stood.  That didn't surprise me.  It brought its claws to either side and clawed at the side of the train, crumpling metal in its massive claws.  My bugs gave me a sense of what was going on as the suit drew the metal into itself with crushing mechanisms and gears.  Its torso expanded slightly as it made room for the new material, armor plates reshaped by internal mechanisms and shifted into place to patch up the worst of the damage.



I arrived on the scene, Imp and Regent only a short distance behind me.  A glance showed me that Bitch, her underlings and her dogs were injured, beaten to the point that they were dirty, bruised and scraped.  Her eyes widened as I approached.



``It won't,'' she growled the words between pants for breath, ``Fucking die!''



I wouldn't have picked a brute-type machine to go up against Bitch, if I'd been in Dragon's shoes, but she'd apparently decided this would be a good matchup.  Or was this Armsmaster's idea?  I was put in mind of the fight at the fundraiser, him trying to not just defeat Bitch, but to beat her into submission.



Not that he was really fighting for a crowd, here.



Or was it something else?  The suit could absorb metal, what would give Bitch that much trouble?



``It's drawing scrap metal into itself,'' I said.  ``Self repairing.''



``I \emph{know}.''



``So stop it from getting the scrap metal.''



``You want to fucking try?''



This wasn't good.  From the moment we arrived on the scene, this suit would probably be signalling others.  We couldn't be sure that Piggot's order to stand down would still be in effect for the other suits, so we had to anticipate reinforcements.  Except this suit seemed to be made to be durable, to stall and wear us down.  It wouldn't be easy to take this down in the limited time we had.



Which was it?  The Melusine?  The whatchamacallit-Nidhug hybrid?  Or was it the Azazel, presumably designed to take on the Nine, with defeating the Undersiders as a secondary design goal?



``We'll try together,'' I said.  ``Regent, we need Shatterbird in here.  Imp, you're backing us up.  Drag the injured to safety.  Did you ever take that first aid class?''



``Grue told me to, but I haven't gotten around to it.''



I swore under my breath.



``Not totally my fault.  Things have been kind of a mess since I joined the team.  Not like there're classes or anything.''



``There probably are.''  I watched the suit step away from the train, adjusting its shape to sort out the additional material it had absorbed into its body.



``Not like it's easy to find classes,'' she clarified.



``Just take care of anyone that gets hurt.  I don't know how much you can do here.  I think one of Bitch's henchmen is over there,'' I said, pointing.



``Okay,'' Imp retreated.



``I'm telling you,'' Bitch growled the words, ``Can't fight it.  It doesn't die.''



``We'll try.  There's got to be a way.  Barker, Biter, you two okay?''



``Hurt,'' Biter said.



Barker nodded, ``Throat's sore.  Keep knocking it down, it keeps getting back up.''



``One or two more tries,'' I said.  ``We hit it with everything we've got.  Bitch, which dogs are least hurt?''



``Bentley and Bastard.  Had a few more I was sending in, but they're hard enough to order around when something isn't hurting them.''



``We'll need their help, then.''



``Bastard's not trained enough.''



I glanced at the wolf cub.  He was five or six times his usual size.  He'd grown rapidly in the past few weeks, but it still meant he was small.  His mutation seemed different from the other dogs.  Was there a whole other department of changes with various subcategories of the wolf breed?



The suit raised one hand, and a chain fired out, a grappling hook on the end.  We threw ourselves out of the way before it could catch any of us.



``Keeps doing that,'' Barker muttered.  His voice was gravelly.  ``Trying to tire us out.  Wear us down.''



``Let's avoid giving it another chance.  Longer range powers first, everyone else close in.''



I hadn't even finished talking before Shatterbird was hurling the glass-coated door into the suit.  She followed up with a veritable tide of glass shards, pulling them from debris and the edges of the street.  The suit staggered back, putting it closer to the train she had just harvested scrap metal from.



``Keep it away from anything metal!''  I reminded them.



Easier said than done.  The area was a fenced in yard with railroad tracks, rusted train cars and trash that ranged from sign posts to disused trash cans.  There was metal to spare.



I was limited in my options.  Bugs wouldn't hurt this thing's metal body.  That left me the less stellar option of fighting it like I had Mannequin.



Barker shouted three times in short succession before bidding the resulting clouds of smoke to detonate violently.  The suit shielded itself with its arms, leaving it defenseless as Bentley flanked and charged it from one side.  It sprawled, landing face down, and reached over to grab two rails from the train track.  In one motion it rose to its feet and hauled two lengths track out of the ground.  Each of the rails bent and folded as they were absorbed into the suit, churned up by grinders and more complex devices.



Bentley charged again, but the suit swung both rails simultaneously to catch the dog in mid-air and hurl him to one side.  Bentley was on his feet in a second, getting his paws under him and lunging for the suit before it could turn to face him, savaging the suit's metal exterior with claws and teeth.



My bugs began to encircle the suit.  The silk had enough areas to catch on, and my bugs were finding openings to crawl within, but I couldn't find much in the way of stuff to interfere with or attack.  The suit's interior was hot, more so as my bugs drew closer to the very center, to the point that my bugs died if they got too far inside.  Everything was solidly made; wires had chain mesh protecting the insulation, pistons and valves were sealed and reinforced, with more delicate technology presumably contained within cases and covers. There was nothing for my bugs to get into.



Using silk to bind the main body wouldn't do anything.  Spider silk had strength on par with steel, but this was an armored suit capable of tearing railroad tracks from the ground and crushing them in one hand.  A material as strong as steel wouldn't accomplish anything against a machine that could rend metal.



I'd have to play this smarter.  I used cords of silk to seal valves shut or bind them in an open position where I could, and focused the rest of my efforts on more strategic deployments, forming cords as big around as my arm.  The suit's arms and legs would be free to move, but my goal was more along the lines of restricting its movements.



Biter used the metal `bear trap' jaw-guard in combination with his ability to distort parts of his body to large sizes, clamping down on the suit's hand.  He had to hurl himself back and out of the way to avoid the suit's retaliatory attack.  As he climbed to his feet, he spat out two fingers and a section of the suit's hand.  I hurried to send my swarm after the discarded parts, using silk and the cumulative strength of the swarm to haul the bits away.



Biter hit the suit twice with enlarged hands and then backed off as Bentley hurled himself into the fray, catching hold of the suit's other arm and hauling on it with all the strength afforded by his muscular forelimbs, neck, jaw and shoulders.  He struggled, \emph{strained, }to tear the arm from its housing.



The suit fought to keep its feet beneath it, leaning hard to one side to compensate for the two-ton bulldog's weight hanging off its arm.  It used its free, damaged hand to grab the dog by the scruff of the neck and flung it hard to one side.



Shatterbird hurled a wave of glass-encrusted debris at the suit.  Not one second after the suit was bludgeoned by the trash cans, wooden planks and pallets, a second wave caught it from behind, striking its legs out from beneath it.



Lying on its back it reached for us and fired another grappling hook.  With the speed it was moving, it looked like it could have caved in someone's ribs, but we each managed to get out of the way.  Some of the people in Bitch's group were moving slower, their reflexes and mobility suffering due to their fatigue.



Okay, this wasn't easy, but it didn't seem as impossibly hard a fight as some of the other suits, either.  It was just a question of keeping up the onslaught, keeping the suit from gathering too much metal for self-repair and hoping that the suit didn't get any reinforcements.  With luck, the other suits would be either on standby due to Piggot's orders or they would be occupied with Trickster, Sundancer and Grue.  Not that it would be a \emph{good} thing if they were fighting, but it would at least mean we got out of here okay.



The suit struggled to its feet, using its arms to shield itself from two more shouts from Barker and a barrage from Shatterbird, then stopped short as the cord of silk I'd bound around its neck pulled taut.  The other end was wound around one of the coupling rods that stretched between the wheels of one rusted train.  I'd worried the coupling rod would come loose, but the elasticity of the silk combined with the durability and sheer thickness of it meant it didn't snap.  The suit was pulled off-balance, giving Biter and Bentley a chance to close in, hammer it into the ground and thrash it.



I glanced at Bitch, saw her mouth set in a grim line.



The suit fought its way free, and Bitch whistled for Bentley to back up.  I could see how it was mangled, metal torn and rent.  Yes, it had displayed some self-repair technology, but every part of it was a ruined mess.  I didn't want to underestimate Dragon's work, but-



Hot steam hissed out from the gaps in the suit, seconds before it turned itself inside out.  The parts on the exterior folded out and were absorbed into the suit's interior, new components emerged from within and locked into place.  They still smoked from the heat of being forged and reforged in the heart of the machine.



The suit's joints shifted position as it settled into a quadruped stance.



I recognized it, now.  It didn't have missile launchers, and it was a fraction smaller than it had been, but it was the same suit Dragon had used when I'd first seen her.  The suit she'd used against Leviathan.  That suit had also peeled apart to reveal a lesser suit beneath.  Presumably it had possessed the same self repair capability and the ability to do what this suit had done, but hadn't had the chance.  Except I wasn't even sure how to define or process what I'd just seen.  It was such an overhaul that I was left grasping for a word to explain it.  \emph{Reincarnation}?



It was easy enough to picture.  Any time the suit took enough damage, it reforged itself into a different shape with the reserve components deep inside its body, or it shed its outer layer, ensuring that it was always in pristine fighting condition.  Give it an opportunity and it harvested metal for raw materials, and it would keep going until its battery ran out.



With the kind of stuff a tinker like Dragon could make, cold fusion reactors and self-sustaining energy sources, that battery could have one hell of a long life.



Either way, it wasn't a new model.  That meant it wasn't the Azazel suit Piggot had told us about.



``You could have explained,'' I said.



``I did,'' Bitch answered, glowering at the smoking suit.  ``I said it won't fucking go down.''



``You could have explained \emph{why}.''



``I don't understand why!''



The reforging process had killed every bug I had on the thing, and it had burned through the silk cord I'd leashed it with.  I was left wondering what the black market price would be for something like Armsmaster's EMP device.  Something that would serve as a get-out-of-a-fight-with-a-tinker-card.



Tinkers had so many options that they brought to the table, a crazy synergy with any teammates, and an ability to customize their approach to counter specific threats or individuals.  \emph{I,} on the other hand, was pretty screwed if I went up against anyone with flame powers, cold powers, electricity powers, enough durability to shrug off my bugs or a way to clear out large numbers of bugs at once.  I'd managed thus far by thinking on my feet, but it sort of pissed me off that tinkers existed as the antithesis of that.



Yes, I was aware that tinkers had to put in hours upon hours of work, and that I only ever really experienced the end results of that investment.  I didn't care.  Whether they had vat grown monsters, clockwork lairs, impenetrable suits of armor, jetpacks and exploding guitars or programs to tell them how to win a fight, tinkers were a fucking pain in the ass.



``New plan,'' I announced.  ``We hit it hard enough to slow it down and then we scram.''



``You want to \emph{run?}'' Bitch asked.



``We don't have a choice.''



``We do,'' she said, still glowering at the suit.  ``We gotta kill this thing sometime anyways, so you come up with a plan like you usually do, we'll make it happen, and I won't have to give up territory to this armor asshole.''



I stared at her, trying and failing to process how she was looking at the situation.  Then it dawned on me.  \emph{This} was why Dragon and Armsmaster had pit this suit against her.  It wasn't that it countered her power, exactly.  It was that it was set up to work against her stubborn nature.  With the way her mind worked, she couldn't back down from a fight she subconsciously felt like she was winning.  It didn't matter that we were losing in the long run, she was focused on the fact that we \emph{could} do damage, and walking away would be a forfeit.



Barker was screaming a long series of invectives at the suit, detonating them.  With four legs solidly on the ground, it wasn't budging, and Barker's shouts weren't doing much to the armor.



``Look at it this way,'' I said, trying to stay calm,  ``We just defeated it.  Heck, every time you've forced it to change like that, that's been a win for you.  How many times was that?''



``Four.''



``Four times, you've kicked its ass.  If you walk away, that's five wins total and one loss, if you can even call that a loss.  But we can't afford to stay much longer, or one of your dogs is bound to get hurt.''



As if to give evidence to my statement, Bentley howled as he grappled with the suit, trying to tear into its neck while the suit attempted to wrestle him down to the ground.  Biter leaped onto the machine's back, his hands with the spiked knuckles worked into the gloves growing larger so he could tear the armor plates away.  Bentley joined in, setting his teeth at the lower part of the armored suit's `spine', for lack of a better word.



Her eyes narrowed.  ``We run?''



``We have to stop it from following first.  One more time, guys!  Regent, stand ready!  We need as much glass as you can spare!''



The suit turned our way.  Three masters, standing in the back lines while we sent our bugs, dogs and lunatic supervillain thrall into the fray.



It began to glow, steaming, and Biter virtually yelped as he threw himself off of its back.  Bentley was slower to react, but he fell back, shaking his head violently as flesh sizzled around his muzzle.



We backed up a few paces as it advanced one step.  It whipped its head up until it almost pointed to the sky, then opened its mouth.  Blue flame streamed over our heads to pool behind us, cutting off our retreat.  We had to scramble for cover before any droplets or sparks landed on us.  I wasn't sure if it was flame at a temperature I wasn't used to seeing, if it was a liquid accellerant that just happened to be on fire or if it was plasma, but I didn't want to touch it and find out the particulars.



All of us, dogs, Barker and Biter included, headed inside a building to seek further cover.  The structure rumbled as the suit climbed the side and settled on the roof.  The A.I.s liked high places, it seemed.



``Need to hit it hard,'' I said, my voice pitched low so the suit wouldn't overhear.  ``One good hit.''



``We don't have one good hitter,'' Imp said.  I turned my head to see her crouching by the vet and one wounded dog.  ``Maybe Shatterbird, but everyone else is about a lot of littler hits.''



``We need one good hit from someone who isn't Shatterbird,'' I clarified.



``Can't,'' Biter said.  ``Limit to how big I can grow myself before I do permanent damage.''



``Define permanent damage.''



``Stretch marks, scarring, permanent aches and pains.  I have some in my midsection, all day, every day, it hurts.''



``Okay,'' I said.  ``Barker?''



``I can't hurt the fucker.''



``You screamed something like three times, then detonated that smoke you make whenever you make noise.  Can you do it more?  More shouts, louder?''



``At my limit.  Probably not.''



``Bentley's hurt,'' I said, ``What about Bastard?''



``He'll probably listen to me, but he might attack anyone else.  He's too dangerous when big.''



``And that suit's dangerous too.  In case you haven't noticed, it's either trying to beat us to a pulp so it can drag us into custody or it's going to burn us alive.  We have to use one of your dogs, and Bastard's in the best shape.  We have to use him.''



Bitch frowned, ``How?''



I told her.  ``You've taught him to fetch?''



She nodded.



``Fetch something big, then,'' I said.  ``Wait until my signal, hit him as hard as you can. Everyone else, let's run for it.''



I could see Bitch tense.  Her henchwoman, the vet, stood and nervously circled around the edge of the room to join us, giving Bitch a bit of space.



``You're leaving me behind.''



``We're counting on you,'' I said.  ``Wait for my signal, then come with Bastard.  More damage you can do, the better.''



All together, we bolted, Bentley following immediately behind us.  I could feel the Dragon suit reorienting to face us, felt it angle its head before it spewed another stream of liquid fire.



\emph{In a residential area?  }This wasn't an occupied area, but\ldots well, the suit might know that.  It might be another reason it was deployed here.



``Hard right!''  I shouted.  We turned to head for a nearby alleyway before the liquid fire even touched ground.



The suit leaped, and I grabbed Imp's wrist, hauling her out of the way.  It landed a short distance from us, then barreled through our group, sending Biter, Barker and the vet-in-training sprawling.



\emph{Controlled movements.  Everything it's doing, it's all calculated.  }Even the more dangerous attacks were geared to hold back just enough to hurt, not to kill.  Even the hurt was fairly minimal.  If Biter had still been on the suit's back when it turned red-hot, I was willing to bet it would have shaken him off to avoid giving him terminal burns.  There had to be something about that I could use.  Trouble was, I wasn't sure when or where the suits drew the line.  I couldn't trust that they'd follow the rules enough that I could offer my own life in the bargain, much less anyone else's.



I signaled Bitch, and she was out of the building in a second.  Bastard was as large as I'd ever seen him, and there was something about his appearance\ldots he looked less \emph{wrong} than the others.  The spikes and ridges of bone that lined his body weren't asymmetrical, and there seemed to be more art to the design.  Drool flew out of the corners of his mouth as he bounded forward, fangs clamped around a wooden post.



The suit was halfway through turning around to face them when Bastard drove the end of the post into its stomach.  It skidded, sparks flying as its claws dug into the pavement for traction.



``Pull it free!''  I shouted.  I didn't wait for her to follow through before calling out the next order, ``Regent, fill the hole!''



Bitch hauled on Bastard's chain and he followed the direction, pulling back, the post still clamped in his mouth.  When it came loose, it revealed a rent in the armor's side, far less empty space than I'd hoped, and a dislodged joint where the leg met the pelvis.



Shatterbird called forth a stream of glass, shoving it into the hole.  I didn't need to give the next order.  I realized she was using her power more through my bugs than any other sign, the telltale high-pitched noise that was above my human limits.  A second later, the suit's rear legs lost their traction on the ground.  Its lower body collapsed.



The suit began struggling for footing.  It was still operational.  I swore under my breath, still backing away.



Shatterbird moved one arm, and the suit slid a few feet in that direction.  She had a hold on the glass.  More forcefully, she pushed it into the nearest building, then dragged it across the alleyway to slam it into the opposite wall.



She repeated the process two more times before the suit tried a counterplan.  It began to reshape itself, glass shards pouring out of the openings as pieces slid in and out.  A third form, something airborne.



Shatterbird slammed it into a wall before it was done reshaping.  The fallen glass shards levitated into the air to find new nooks and crannies to slide into.



The suit was hot, naturally heating up as part of the reincarnation or reformation process.  I watched as glass melted, running into holes and slats in the armor.



Shatterbird pushed again.  The suit barely moved.  She wasn't so adept at moving \emph{molten }silicon.



We continued backing down the alley.  The suit raised its head, preparing to cut off our retreat with another pool of flame.



In her second jousting run, Bitch lanced the thing through the base of the neck.  Fire spilled down around it, setting the post aflame, and the attack was stalled.



She wheeled Bastard around and shouted, ``That's six fucking wins to one!  Go!''



We ran.  I maneuvered my swarm behind me to watch for its approach, felt it step forward and then collapse, its legs giving way.



\emph{Even the forelegs?  }Okay, that was interesting.



The glass.  It had melted, and it was cooling in the lower recesses, farthest from the body's core.



I could have told Bitch she'd beat the suit, that we might have defeated it a hundred percent, but I kept my mouth shut.  Didn't need her acting on what might be a false assumption.  If it freed itself, found a way of reconfiguring where all of the glass-affected areas were contained, or if it simply abandoned its legs in favor of a smaller form\ldots too many possibilities.  Better to leave it and cross our fingers.



Damn tinkers.  What the hell was Dragon's specialty?  The ability to make stuff without half the time other tinkers would need?  So many different suits, so many different projects and tasks, and it rarely interconnected, if ever.



We ran two or three blocks before we had to stop.  Shatterbird sent glass shards into a nearby door, then tugged it free.  A sled for Regent and Imp.



With some coaxing, I got the vet-trainee to climb onto Bentley's back.  The other henchman, the guy, climbed up behind me.  Barker approached Bastard, and received a mean growl in response.  We searched for an option for Barker and Biter before Regent and Shatterbird offered another door.



We made good time on our way to Ballistic's lair.  We'd planned to arrive by dusk, but the sun wasn't even setting.



The others weren't there.  We double checked, then mobilized to find them, spreading out.  With reluctance, I drew my relay bugs from the interior of my shoulderpad.  I felt a twinge of disappointment as I handled them, gently passing them on to dragonflies that could carry them.  They were dying.



Panacea hadn't given the relay bugs a digestive system, and in my haste to save Atlas from a slow death by starvation, I'd neglected to pay attention to them.  It wouldn't have mattered anyways, probably, because Grue had only had so much time to work with.



The dragonflies sent my relay bugs out so I could keep in touch with the others as we searched for Grue, Trickster, Sundancer and Ballistic.  Bugs were tough, natural survivors.  I knew that cockroaches could survive lengthy periods of time without heads, that other bugs could be frozen solid and thawed and be little worse for wear.  They subsisted on relatively little food considering their body size, and the relay bugs had held on this long with an inability to eat at all.  Their physiology wasn't quite the mess that Atlas's was, and they retained some basic hibernation instincts, defaulting to a near-immobile state.  It was a struggle to even get them to extend my power's range for me.



I found the next dragon suit before I found the others, and I immediately knew it for what it was.  It had to be Azazel.





