





If I was remembering right, the Slaughterhouse Nine had introduced themselves to their prospective members roughly two weeks ago.  I couldn't be sure what had happened, but Piggot had alluded to the idea that Armsmaster had banded together with Dragon.



Two weeks, and they'd built \emph{this.}



The other dragon suits had the general stylings of dragons, with claws, armor plating that resembled scales and heads or faces that resembled a reptile.  In the end, though, they were still machines, and the theme was just that.  A theme.



Rather than armor plates, the scales were fine, intricately detailed and arranged with a kind of natural sense to it, with denser scaling in the areas which saw the most movement, creasing and folding and heavier scales around the elbows, talons and face.  There were wings, batlike, with openings at the base of each `finger' that the membrane stretched between.  The actual body was more like a lizard, but the angle of the forelimbs and shoulders resembled those of a human.  When Azazel moved, its scaled exterior rippled with the shifting movements of the mechanisms underneath.



My bugs found their way inside, and I discovered it was very different from the machine we'd just fought.  It wasn't sturdily built, nor was it solid.  The wires and internal mechanisms weren't heavy-duty, reinforced or covered in chain mesh.  They were so numerous and dense that I couldn't hope to make any headway with every bug in the city committed to the task.



It was, just going by what I could tell from my swarm-sense, a machine as intricate and multilayered as a living, organic being.



But how?  It didn't make sense in terms of the timeframe.  It would have taken time to make each individual, unique part with their condensed and intricate design, but he'd only had two weeks.



A thought dawned on me.  It was a half-formed thought up until the moment I devoted some attention to it.  Then it clicked.  Tinkers had a knack, a specialty, be it a particular field of work or something they could do with their designs that nobody else could, and I knew Dragon's.  She could intuit and appropriate the designs of other tinkers.



It put everything in perspective.  The machines she was using, half of them drew on ideas I'd seen other tinkers put to work.  The drone model had used Kid Win's antigravity generators and Armsmaster's ambient taser, the wheel-dragon might have used the same theories as the electromagnetic harness Kid Win had been packing when we attacked the PRT headquarters.



It also served to explain how she could invest the time to make the suits.  If her power afforded her the brainpower and raw thinking power to understand and apply the work of other tinkers, then she could put all of her resources towards manufacturing.  Armsmaster made the base design, she appropriated it and then turned artificial intelligence or her own power to creating the necessary variations.



I could imagine how she had worked herself into the Protectorate and the Guild for just this reason.  It would get her the funding and raw materials she needed.  Being a member of the team would give her access to the work of the various tinker heroes, in the name of oversight and security.  Add the confiscated material from criminals like Bakuda, and she had unparalleled access to other tinkers' work.



There were realizations that were kind of a `eureka' moment, except not so much an inspiration borne of creativity or creation as being about finding that weak point, finding that way out of a corner.  This wasn't one of those.  This was one of the realizations I wish I hadn't had, because I could feel my own morale plummeting.  If I was even close to being right, then Dragon was the \emph{incarnation} of why tinkers were so dangerous.



Which didn't change the fact that we had to find a way to stop her or everything we'd worked for would be for nothing.



I used the relay bugs to extend my search out further, and ran into a snag.  My swarm died in droves, bugs being obliterated or having half their bodies sheared off as they approached too close to what the suit was building.



It slammed one claw down, and my bugs could sense a thin rod skimming along the surface of the ground, tracing bumps and depressions.   The telescoping rod extended several hundred feet, crossing from the corner of one building to the base of a wall on the other side of the street.  It stopped, and there was a pause as the suit moved on.  Then the rod \emph{bloomed}.



There wasn't a better way to put it.  It expanded, unfolded, the rod of metal peeling open like a stick of bamboo, leaves and shoots unfolding over miliseconds.  The final stage, what I might call the `flowering' was familiar enough.  If I could see it, I'd describe it as a vague blur.  Armsmaster had used the effect for the weapon he'd used to hack away at Leviathan, and Mannequin had been in possession of a knife with the same effect.  Except these blurs were five or six feet around.



I watched as the suit scanned the area, its head sweeping right to left to survey the area before it planted two more.  One extended for what must have been a tenth of a mile before it met another wall and stopped.  Since I'd been watching, four streets had been rendered impassable.



What did the Undersiders and the Slaughterhouse Nine have in common?  Besides our general intimidating natures and disturbing powers, we were both elusive, favoring hit and run tactics with a degree of shock and awe to keep our enemies off-balance.



Dragon and Armsmaster had decided on this as their means of attack.  They would seal off our movements by erecting barriers that were the high-tech equivalent of barbed wire.  Barbed wire that would turn steel into vapor.



That wouldn't stop Siberian though.  What technologies had I seen that they might use against her?  Or was it a technology I hadn't seen before?  There were some ugly possibilities there.  Something long ranged that could take him out before he could get to cover?  A microscopic form of attack that could fill the air and debilitate him if he wasn't in an airtight container?



``What's wrong?'' Bitch asked.



``Found it.  Trying to find the others but I'm running into a bit of a snag.  The suit's setting up barriers.''



``The forcefield thing they sent against Sundancer?''  Regent asked.



I shook my head.  ``I think it's the Azazel suit the Director mentioned.  It's using that blurry stuff that cuts through anything, I told you about it.''



``I don't remember that,'' Imp said.



``Just don't touch it,'' I told her.  ``Not even in a joking way.  You're likely to lose your finger or your hand before you realize something's wrong.''



``Uh huh.''



``I thought these things were supposed to be packing \emph{nonlethal }hardware,'' Regent said.  ``Blue fire and now this?''



``I don't know,'' I said.  ``The Director said these suits were supposed to go up against the Nine.  You want to be as lethal as you can get.  I- I'm pretty sure they're holding back, though.  They could have hit us a few times and didn't.  We might be able to use that, but that's testing our luck.''



``What?  You're thinking about a kamikaze attack?''  Regent asked.



``Probably not.  We don't know everything that suit could be packing in terms of devices or hardware.  Especially with Armsmaster helping out.  It's definitely going to have something they think can counteract Siberian, so let's rule out a brute force attack.  The hedge maze it's building would hold off Hookwolf or Bonesaw's creations, and the sturdiness of the design would protect it against Jack.  In terms of other tactics the Slaughterhouse Nine might use\ldots hostages.  I'd bet it's packing containment foam.''



``So what \emph{do} we do?''



``It's still a machine, a well made machine, but it's a machine.  We can break it, given an opportunity.  But our number one goal is going to be keeping it from catching us out of position and walling us in.''



``We could move up to the rooftops,'' Regent said.



``I have a bit of a policy against doing that,'' I replied.  ``It leaves you with a shortage of escape routes.''



``Doesn't sound like we'll have many anyways.''



``No.  But we'll worry about that when it comes up.  Worst case scenario, we climb for the rooftops when it happens.  The dogs are mobile, and I assume Shatterbird can lift one or two people at a time?''  I asked.  Regent nodded confirmation.  I continued, ``For now, we'll take the long way, keep our distance from it, see if we can't find the others.''



I looked around, saw some nods.  I glanced at Bitch.  Would she see it as cowardly?



``Okay,'' Bitch said.



``Good.  Let's leave your people behind?  No use bringing them into a fight.''



She nodded.  I looked over my shoulder at the vet trainee and the guy, and they took that as their cue to climb down.



The remainder of us rode.  Me on Bentley, Bitch on the wolf cub's back, Barker and Biter riding in tandem on one door just behind Regent and Imp on the other.



The machine was gradually taking over an area near Ballistic's territory with the disintegration `hedges'.  Going counter-clockwise around Azazel would have meant running face first into the crater Leviathan had made.  Traveling the edge threatened to put us dangerously close to the suit, and with the water on one side we'd have denied ourselves one of the cardinal directions as far as escape routes went.  That meant we were left with only one viable route to travel if we wanted to head further into the downtown areas; turning left and giving the suit as wide a berth as possible.



I kept one metaphorical eye on the suit as we traveled, while sweeping out with my swarm to scan for the others.  Azazel was laying down more of the `hedges', not connecting them but placing one and then winging past intersections and streets to place another two or three blocks away.  I couldn't be sure what the point was.  Our teammates were nowhere nearby, as far as I could tell, and the openings were wide enough that the barriers wouldn't really hamper us even if we were running straight through the area.  Maybe a bit if my power wasn't informing me of where we needed to go, but even Bitch would be able to get by without too much trouble.



I couldn't shake the notion that I was missing something.  Was there something about those rods that I wasn't aware of?  None of the rods were any thicker around than my pinky fingers, so they didn't leave room for any real traps to be hidden inside, Armsmaster's special talent or no.



It had been too long since I rode one of the dogs.  They weren't well suited for riding, and that was doubly the case with Bentley, with his broad shoulders and barrel-like chest.  It forced my legs apart, and that made for an uncomfortable ride when coupled with the bouncing motion as he ran and the lingering soreness of my shoulder from the battlefield surgery Brooks had provided.



I thought about calling for a break when I noticed movement.  Not Azazel.  It was coming from the other direction.  My heart sank.



The drone-dragon.



``Incoming!''  I called out, using my bad arm to point in the general direction of the approaching suit.  It was approaching at a right angle, accurately enough that I feared it had a way of tracking us.



This was one of those moments where I had to make a clutch decision as leader, but it seemed like a choice of a half-dozen equally awful options.  Splitting up, moving closer to Azazel, trying to confront the drone deployer, hiding and risking getting cornered?



\emph{Damn}.



I wondered if I was maybe better at improvising than I was at spur-of-the-moment strategy.   There was a distinction there.



``This way!''  I shouted.



Running straight down the road left us dangerously exposed.  I led the group down a diagonal route, zig-zagging between alleyways and the main streets.  Away from the drone-deployer and slightly towards Azazel.



When Azazel shifted positions and took flight, heading straight for us, I was left to wonder if that had been their plan all along.



``We're being herded!''  I called out.  ``Reverse directions!''



I hauled hard on Bentley's chain, getting him to turn, then goading him to start running the way we'd come.  Regent, Imp, Barker and Biter had a harder time.  The `sleds' were too dependent on momentum, and they didn't have built-in traction.  Bitch and I pulled ahead on our respective mounts while the others tried to get turned around and build up speed again.  We couldn't afford to stop and wait for them.



The drone suit flanked us on our right, drones spilling out of its ports to trail behind it like my bugs trailed behind me.  Other drones were moving to cut us off in front.  Azazel was behind us and to our left.  The herding was still underway – the sole route left to us, if we didn't want to run straight into a mess of drones or one of the suits, would be going left.



Left took us into the area Azazel had employed the rods and the `hedges'.  Fuck that.  I could see what Azazel wanted to do, now.  The moment we were in there, it would take flight, setting down rods to close the gaps and trapping us inside.



My swarm and my eyes scanned the area.  In a matter of seconds this decision would be made for us.



I saw what I was looking for.  A third option.  If I was eyeballing this wrong, or if Bentley didn't have a hard enough head\ldots well, one of us would get hurt.



``Go!'' I urged the mutant bulldog on, steering him for the nearest building.  He pulled away, and I steered him back on course, ducking low so I was hugging his neck as I drove him forward into the already ruined display window of a minimall.  I could feel the top of the display window scraping against the armor on my back as we passed through.



We stampeded past a store that had already been looted, headed for the glass window that faced the mall interior.  If I could find a shortcut through here, exit on the far side of the drone-dragon, we would be able to make a break for it.  Shatterbird could drag the two sleds faster than the dogs could run.  She wasn't that fast: I could remember how she'd fallen behind the rest of the Nine in the fight where we'd taken her captive.  Still, they could fend for themselves for just a little while, while Bitch and I got some breathing room to prepare a counterattack.



The drone-deployer could see what I was doing.  Drones were moving down to cut me off.  Cut \emph{us} off, as Bitch had followed.  Bentley and I crashed through the store entryway and into the mall proper.  It wasn't a big place, and the interior was riddled with tents where some people had holed up.  Store owners wanting to protect their goods?  The area was empty now.  Had Azazel evacuated it?



I could sense two drones orienting themselves to bar our way, and steered Bentley between them.  Twenty or twenty-five feet of distance would be enough, if there wasn't anything to conduct the ambient electric charge.



There was.  Bentley and I were rocked as both drones fired off at once.  The dog took it harder than I did, and we sprawled.



Bitch slowed as she approached.  She started to head my way, maybe to rescue me, maybe to help Bentley, but I could sense a drone moving straight for me.



``Go!''  I shouted.



She turned and ran, the third drone turning to pursue her.  It was too slow.  She, at least, would get away.



I couldn't say \emph{why} the electricity had reached me.  I'd thought I'd figured out their basic range when I'd first fought them, but maybe the simultaneous effect had extended the charge between them?  Or there was something nearby that had helped carry the charge, something in the tents or the mall's design?



Through the plexiglass that framed the mall entrance, I caught a glimpse of Azazel.  The scales that covered it were small and dark, glossy, and the spaces between them glowed like hot coals, red and orange.  Its head paused as it glanced through the window, and a red eye fixed on me.  It stamped one claw down on the ground, in a movement my swarm had felt too many times.



\emph{No}.



The rod extended beneath me before I could climb to my feet.  In one second, smaller branches had extended under, over and around me.  One more second passed, and they bloomed into the blurry effect.  Bright red, orange and purple, as if to signify the danger it posed in the most basic, primal sense, like the yellow of hornets or the bright red of poisonous berries.



I froze, afraid to even breathe.  I was still in one piece.



Tentatively, I commanded some of the bugs out from beneath my costume.  The insulation had protected some, luck and sheer durability had saved a scant few others.  They died the second they moved more than an inch away from my body, vaporized.



My heart was pounding from the recent exertion, adrenaline still flowing through my veins.  As I realized the situation I was in, my body was shifting into fight or flight mode, but humans weren't engineered to go into the same `deer in the headlights' state like conventional prey animals.  And that was what I needed to do.  I needed to freeze, not to fight, struggle or run.



My lungs screamed for oxygen, and I let out a small breath.  It came out as a half-whimper.  I watched as one lock of hair shifted from where it was draped over my shoulderpad, slipped down to touch the blurry growth that surrounded me.  It turned to dust, and I held my breath yet again, afraid I'd inhale the vaporized hair and cough.



Azazel was taking the long way around the building, heading into the same storefront I'd ridden Bentley through.  It wasn't huge, but it was big, and its progress was agonizingly slow.



I'd been on my hands and knees for ten seconds, maybe twenty, but already my body was feeling the strain, screaming at me to change position.  A crease on the inside of one of my kneepads was digging against the bone of my kneecap.  The branches that extended around me \emph{might} hold me, but they might not, either.



And there was nobody even close by.  If this was the movies, it would have been an opportune time for Tattletale to make her move, but we'd already been that fortunate \emph{once}, with Imp forcing Piggot to order a standby.  I couldn't hope for a second lucky save.



Azazel was moving through the store now.  It was a minute away, as it carefully planted its feet to avoid crushing store merchandise.  I wanted to scream at it to move faster, that I was afraid my hand would lose traction on the dusty tile and slip into the disintegration effect.  I could lose a limb like that, or belly-flop onto the blur beneath me, bisecting myself.



Why hadn't it cut me when it grew?  Because whatever guided the growth kept it from tearing up the surrounding material.  It was why the Halberd and dagger hadn't been destroyed by the growth of the disintegration cloud around them, why the growing `hedges' of the stuff hadn't cut out sections of building.



I wasn't in immediate danger, besides the obvious, so I decided to try something.



``I'm going to fall!'' I screamed.



I could sense Azazel lunging forward, crushing a store display as it hurried to the opening, its mouth opening.  It directed a blast of superheated air at the ground, so it cut through the lowest portion of the disintegration hedge, clearing the area beneath and around me.  I winced at the heat of it, but took it for what it was.



``\emph{You may lie down but do not try to move from your current location, Skitter},'' the machine spoke.  It was the same voice as the armbands and drones, but deeper.  ``\emph{Do not stand or make dramatic movements or you may be harmed}.''



The message delivered, Azazel began spraying Bentley down with containment foam.



I checked with my remaining bugs.  A bubble with a four-foot radius had been cleared around me, but the larger branches still existed and a rough dome loomed over me.  The area where the hot air had been vented in made for an area I might have been able to fit an arm or leg through if I felt brave, but I wouldn't be able to crawl through, not with the branches being where they were.



``You assholes aren't holding back,'' I muttered.  When the suit didn't respond, I glanced up.  It was standing stationary above me, apparently content to have \emph{me} and me alone.



My allies were still making a run for it.  The drone ship pursued Shatterbird, Regent, Imp, Barker and Biter, and some stray drones were chasing Bitch but falling behind.  I positioned the relay bugs to keep in touch, but didn't know what to communicate.  That I was captured, but they shouldn't come back for me without a plan or reinforcements?  Bitch would let them know.



No, I was stuck here, in custody.



``So, she design you to talk?''  I asked.



Silence.



``This statement is false,'' I told it.



``\emph{I'll go with true.  There, that was} easy,'' Azazel replied.



Damn.  Wouldn't be able to shut it down with paradox.  Dragon apparently had a sense of humor.  The reply sounded canned, a recitation.  Or she had a liking for popular culture I wasn't aware of.



\emph{Think, Taylor, think!}  What were my options?  I had bugs, but they wouldn't be able to do anything.  I drew them closer, wary of the two drones that were picking themselves off the ground.  Bentley was down.  My weapons wouldn't cut me free, and I was leery of trying to use my weapons on the larger branches, in case I brought something down on my head.



Armsmaster had called it nanotechnology.  It cut through anything, everything.  If some dropped free and fell to the ground, would it keep falling, cutting out a bottomless pit?



No, I needed to find and exploit weaknesses.  If my costumed career had taught me two things, it was that things could always get worse, and there was always a solution.  It was, in a way, why I wasn't freaking out over the end of the world.  I'd already accepted that things could get bad, and I held out hope that we could find a way out.



I could find a way out here.



The suit had used a heat gun.  Was the nanotech vulnerable to heat?  To fire?  It would be ironic in a way.  The growth around me resembled fire with its hues and blurry, transparent nature.  Fire frozen in time.  The entire scene made for a strange picture.  Azazel and its `fire' weren't moving in the slightest, and the only things that \emph{were} moving were the two drones that were rotating lazily around Azazel and the clouds of dust that had been stirred by the blast of hot air.



With my swarm, I felt around my utility compartment.  Yes, I had a box of matches.  I'd packed tissues in there to keep them from rattling around, like I did with my changepurse, so I'd have to use my hands to withdraw them, probably.  The suit wouldn't let me once it saw what I was doing.  I wasn't sure what the response would be, but it could range from blasting me with containment foam the second the fire ate at the nanotech to hitting me with that superheated air to blow me into the side of the dome, vaporizing me.



Had to deal with Azazel first.  I looked up at the reptilian face with glowing red eyes.  I could see the snakelike neck, the human-ish shoulders and arms.  It looked more like a demon than a dragon, from this perspective.



The only weapons I had were my bugs.  There weren't enough in my range, even with the relay bugs, to do anything to the suit.  The model we'd just fought in Bitch's territory had been able to bend steel, would have been able to tear my spider's silk.  I couldn't hope to tie \emph{Azazel} up.  It was bigger and I was willing to bet it had more raw strength.  Maybe it was better to say that I was confident enough it had more raw strength that I wasn't willing to take the risk.



No, my bugs wouldn't serve.  I sent some cockroaches in to see if they could nibble through the insulation of some wires, but it felt futile.  Even in what stood to be the more vital areas, like the neck, I doubted my ability to do any real damage.



What other tools did I have?



My voice.



Dragon was smart.  Smart enough to write an A.I. that wouldn't crumble to a simple issue with paradox.  But the A.I. wasn't necessarily brilliant.  It had leaped to my defense when I'd said I was in danger.  Either it wasn't smart enough to discern truth from a lie, or it wasn't \emph{allowed} to when a life was potentially in danger.



I'd wondered if the machines were obligated to preserve our lives.  Now I had a better sense of it.  Now how to use it?



Regent and Imp were still fleeing the area on one of Shatterbird's sleds.  They had outpaced the drone ship, which was moving too slowly to pursue even Shatterbird.  It was better suited, it seemed, for seizing and protecting an area than for pursuit.  Good.



I drew out a message on Regent's back.  `Hide'.  Imp was directly behind him, and bugs on a white shirt would be clear as day to her.  I hoped.  They were almost out of my range, relay bugs or no.



``You're Azazel, correct?''



``\emph{Correct.}''



``What's the other ship called?''



``\emph{The Glaurung Zero is an old model, designed to deploy drones of varying loadouts.}''



``Thank you for the information.''



``\emph{You're welcome}.''



``Don't suppose you'll tell me how to defeat you?''



``\emph{No.}''



``Or your self destruct code?''



``\emph{No}.''



``What if I told you that you were putting a human life in grave danger?''



``\emph{I have no reasonable cause to believe that.}''



Damn.



But if it wasn't designed to tell truth from a falsehood, maybe\ldots



``Imp had a second trigger event.  She should be invisible to your sensors.''



``\emph{I have no reasonable cause to believe that.}''



``Doesn't matter.  Imp may be in this room.  If you move a foot, you could be stepping on her.''



``Imp could not be in this room.  As of two minutes ago she was recorded at a distance of .4 miles away from this location.  She could not return here in that span of time unobserved.''



The suits were communicating.  That was good to know, but it wasn't exactly \emph{good}.  It made this harder.



``She could if Trickster leapfrogged her here,'' I said.  If Trickster was currently engaged in a fight with one of the other models, this could blow up in my face.



But the suit didn't refute me.  It didn't speak at all.



``I used my power to signal Imp and Trickster and ask them to help.  They're nearby, and it's very possible Imp is here.  She could be crawling on top of you, for all you know.  If you open your mouth, move your head or move a wing, you might be causing her to fall.  With your head being where it is, it's not impossible she could fall and roll into this nanotech hedge you've made, right?''



I waited for a response, for the canned reply saying Azazel had no reasonable cause ot believe it.  Nothing.



Had it worked?



``Maybe I should be more specific,'' I said.  ``I told them to help in general.  They might not be helping \emph{me, }so it's very possible that any other suit might be in immediate proximity to Imp.  Be careful you don't accidentally crush her.''



No reply.  Hopefully that would help the others somehow.  It wouldn't stop any of the ones in the air like that Glaurung drone suit, but it could stall others.



``Now,'' I said, picking my words carefully, my pulse pounding, ``I'm going to light a match and try to burn this thing away.''



I drew the matchbook from behind my back, grabbed a match from the box.



Hesitated.



If the hedge burned quickly enough to matter, what would happen?  Azazel could easily spray me down in containment foam.



I began organizing my bugs, placing them on the ceiling, drawing out lines of silk cord.



The PRT could be entering my range any second, ready to take me into custody.  I needed to be fast, but I couldn't rush this.  I was replicating the natural design of a spiderweb, three times over, but I was making each strand fifty or sixty times as thick, braiding other threads into cords and braiding cords into thicker strands.



It took a minute before I was satisfied.  I was aware of the drone that hovered some distance over my head.  I adopted a general runner's pose, then lit the match.  With my bugs, I was able to sense the safe distance I could raise my hand, match held high.



It burned faster than I would have thought.  With a whoosh like I might expect from lighting a barbecue, it was gone.



A series of things happened in that instant.  I pulled free of the branches that hadn't burned away, sprinting for the exit,  Azazel opened its mouth and began spewing containment foam, and the drone began speaking, ``\emph{Attention Citizen\ldots}''



I maneuvered the spiderweb-nets into place in the stream.  Two were far enough away to catch only a little, but the burden was heavy, growing more awkward for my bugs as the expanding foam captured some and rendered them unable to fly.



I still managed to drag the foam-nets into place, covering one drone's eye-lens and the other's gravity panel.  They spiraled out of control, one striking a column, the other plummeting for the ground.



The other net was fixed just in front of Azazel's mouth, strands already wound around the scales of its face.  It tore free on one side, but the foam expanded, forming a beard, then covering its mouth.



The makeshift barrier had kept the worst of the foam from reaching me.  I scrambled out of the way of the rest, narrowly avoiding getting the damned stuff on my costume.



Azazel's chest opened, and a grappling hook speared out.  Still trying to recover from dodging the foam, I couldn't dodge it.  It seized me, and I hurried to climb over the railing that surrounded the now-empty fountain to keep Azazel from drawing me up into its chest.  Or into the foam that wreathed its head.



I climbed under the railing, to see if I could wind it up any further, then jerked to a stop.  The hook was frozen in midair, still clutching the armor at my chest and shoulder.



Right.  So this was how they'd planned to counteract Siberian.



I couldn't free myself, and I couldn't fight back, so I waited.



Armsmaster had said this technology drained his batteries, but Azazel could have a major power source in its chest.



It took only a minute before the hook went limp.  I managed to pry myself free.



Other than opening its mouth to spray the foam and turning its head, Azazel hadn't budged from its position.



With my swarm, I signaled Regent and Imp:  `Good job.  Come back fast.'



Without Bentley, I couldn't cover enough ground.  Couldn't run.  I found a hiding spot by the mall entrance instead.  From the spot, I used my swarm to covertly keep an eye on Azazel, praying that whatever Dragon was doing was consuming her attention.  Praying that she wasn't about to override the simple head game I'd pulled on her hyperadvanced mecha-suit.



\sectionbreak



A \emph{very} satisfying crunching noise rang through the minimall.  I stood there, watching in approval with my arms folded as Grue, Sundancer, Ballistic and Genesis approached.  I'd signaled Trickster to tell him to stay back.  No use giving the suit a way to rationalize its way out of my lie.



``Is that the Azazel?''  Grue asked.



``Yeah,'' I replied.



``It's not moving.''



``Because I told it that it might crush Imp if it did.''



``Ah,'' Grue answered.  He didn't ask for clarification.



``How'd it go?''  Regent asked.  Azazel had started venting the mist to clear away the containment foam, freeing its head and front claws where it had been covered in its own foam, but I'd already formed a mesh of spiderwebs to keep it from opening fire with any of its weapons.  The mist had also exposed enough of Bentley for us to save him.  Working together, we'd already cut the real Bentley free of the desiccated flesh of his larger self that contained him.  The bulldog and Bastard were happily sitting between Bitch and I.  Shatterbird was hammering at Azazel, smashing it repeatedly with a massive wrecking ball of condensed glass.



Sundancer spoke up, ``We took down the hybrid model.  Giant gun, was sitting in the stratosphere, shooting down Genesis every time she sent a body out into the open.''



``Our group took down \emph{two},'' Bitch said.



``Where are the others?  Shouldn't more reinforcements be arriving?''  Grue asked.



I shrugged, ``If they come, I'll know, and we can react.  We've gotten this far.''



A minute passed, punctuated by the thud of the glass sphere against Azazel's outer body. Only a little damage was done with each hit, but it was adding up.  That, and it felt good, in a way.



Sundancer created an orb of flame and drove it into Azazel.  I watched as the metal melted and the wiring burned in clouds of acrid black smoke.  In the span of a minute, the suit was slag.  I signaled Imp and Trickster to tell them it was okay to approach.



We watched the suit burn.  Trickster and Imp joined us from the outskirts of the mall.



``I feel bad about this,'' I said.



``Why the fuck would you feel bad?'' Bitch asked.



``They must have put millions into manufacturing this.  That was supposed to stop the Nine, and It was powerful enough that it \emph{might have}, if it'd had Dragon's brain backing it up.''



``They can build more,'' Grue said.



``Scary thought,'' Sundancer commented.



``We got lucky,'' I said.  ``What with Imp being able to force Piggot to shut them down, and the way I could exploit it's A.I. to lock down its movements.  Maybe you can make a program versatile and leave yourself open to the program using loopholes to work around any safeties you put in place.  \emph{Or} you can make it heavily restricted and leave it open to vulnerabilities like what I exploited there.  I guess we're a ways off from an A.I. being smart enough to work around those limitations.''



``It's a matter of time,'' Regent said.



``You're such a pessimist,'' Imp retorted.



``And I'm so \emph{right}.''



The suit continued to burn.  Containment foam billowed out of a container within Azazel's body, putting out the worst of the flames and leaving us with an assurance that Azazel wouldn't be lurching back to life the second we turned our backs.



``Let's go,'' Grue said.  ``Four more suits to take down, and we don't have long before it gets dark.''



I nodded.



We were half a block away from the minimall when a phone rang, startling the living daylights out of us.  It was my satellite phone.



\emph{Dragon?  }



Tattletale: ``Phones are back on.''



``Why?  Is she baiting us?  Trying to get us to reveal our positions?''



``She's gone,'' Tattletale replied.  ``Suits leaving the city, satellite phones are working.  Few factors at play, there.  I got word back from the Dragonslayers.  Paid them a few million bucks to tell me how they keep getting the upper hand on Dragon, tell me how she's relaying commands to her suits.  With that, I had some squads plant C-4 and knock down cell towers.  That slowed her down, cut her bandwidth, so to speak, and limited her ability to reprogram them on the fly.  I'm guessing you guys took out one or more suits?''



``Three,'' Bitch said.



``Two or three,'' I clarified.



``That cost the Protectorate a good chunk of cash, and it's detracting from Dragon's primary mission, which is the Nine.  My guess is she's zeroing in on them.  Better to have a few suits closer to where she thinks they are than to leave them here in the city for you guys to keep breaking.  So she thinks, anyways, and the bigwigs that are footing the bill seem to agree.''



``I can live with that,'' I said.



``I think we all can.  It doesn't mean there won't be more coming down the road.  But whatever else she does, she won't be able to sell the local government on the idea that victory is a hundred percent assured, and she'll have to justify the costs to the PRT.  That means we're getting a reprieve.  When she \emph{does} come back, it'll only be because she's \emph{certain }she can win.''



I glanced around at the others.  ``That's good to know, kind of.''



``What's important is it won't be in the next little while.  If they intend to send someone like Eidolon or Alexandria here, even, it won't be anytime soon.  So I can give you the official announcement.  We won.  Job complete.  The Pure have hauled ass out of town, Faultline's apparently decided it's safer to be out of the city, and you've humiliated the heroes enough that they can't honestly contest your claim.  There's nobody left.''



``The city is ours?'' Grue asked.



``The city is ours.  And here's the thing.  Order from the one in charge,'' Lisa paused, and her meaning was clear.  An order from Coil.  ``You're done.  Good job.  Your final order for the time being is to take a few days off.  No costumed tomfoolery.  Go back to your territories, make sure things are okay, but no getting into fights.  If I see you out in costume, you're fired.  Hell, I'll shoot you.''



It sounded like a joke, the way Tattletale put it, but the deeper meaning was clear.  Coil was telling us to stand down.  No matter what.



``Just like that?'' Grue asked.



``Yeah,'' Tattletale said.



``I was going to go out,'' I said, ``Uncostumed, don't worry, but um-``



Didn't want to say \emph{where} I was going on a line the heroes might be listening in on.



``I get it,'' Tattletale said.  ``I know where.  One sec.''



A pause.  No doubt while she checked with Coil.



``Okay.  Cool,'' she said.



``I can go?  It won't cause issues?''



``No issues.  So long as you-``



``I know,'' I cut her off.  So long as I left the costume at home.



``We'll talk later,'' she said.  ``Gonna go see if I can get more details on what happened.  Betting \emph{someone} blew their top when they realized you guys demolished two of those suits.''



``Three,'' Bitch said.



``Sure, three,'' Tattletale clarified.  ``Ta ta.''



She hung up.



Our group paused, each of us looking to the others, as if we couldn't believe it, or we were measuring each other's reactions.



We'd won.  We'd cost the PRT too much in resources, pride and money, and they'd apparently decided it wasn't worth their time to uproot us.  I hated the bureaucracy, the fucked up mindset of the institutions, but it was clearly working in our favor here, at least.



Coil had his city.  There was nothing more I could do.  The only thing stopping Coil from following through on his end of the deal and releasing Dinah was, well, \emph{Coil}.



I exhaled slowly, letting out a deep breath that I felt like I'd been holding in for a month.





