





``We should throw a party,'' Imp said.  ``Celebrate.  Rub it in a little.''



``Rub it in?'' Grue asked.



``Yeah.  Party in the streets, maybe some fireworks.  Show the heroes that we know we won and we're doing fine.''



There were a few chuckles from the others.  Regent and the Travelers, primarily.



``In what way is that even \emph{close} to being a sensible idea?''  Grue asked.



``I didn't say it was sensible.  But it's fun, and that's why we got into this, right?''



``No.  No it isn't.  It was maybe a side-bonus when \emph{I} joined the group, if anything, but things have changed since then.  I warned you this would be hard work, that it \emph{wouldn't} be fun and games.  And throwing a party to celebrate a win is a monumentally bad idea when we don't even want the heroes to know we consider this victory anything out of the ordinary.''



``It \emph{is} out of the ordinary.  We're not giving anything away if we're celebrating scaring off \emph{Dragon}.''



``I kind of have to agree,'' Regent chimed in.  Grue turned his way, and I could imagine the death glare that was behind his mask.  Probably scarier than the mask itself.



``Maybe you're right,'' Grue said, ``\emph{Maybe}, I won't say you're absolutely right there-''



``Of course not,'' Imp said, sighing.



``-But we definitely don't need to rub it in the heroes' noses.  Not if it means they have both an excuse and motivation to try this again, \emph{sooner}.''



``If you're afraid of that, we'll \emph{never} be able to celebrate a win.''



``I'm okay with that,'' Grue said.



``Do we get to chime in?'' Trickster asked.  ``Because I'm siding with the Imp, here.  Morale could become pretty important if we're going to be building up individual gangs and collections of henchmen.''



Grue sighed.  ``Feeling outnumbered here.  Skitter?''



``What?''  I blinked.  ``Sorry, not keeping track of the conversation.''



``She's out of it.  Tattletale broke Skitter when she said we won,'' Regent said.



``I'm\ldots I'm alright.  Lost in thought''



Grue settled a hand on my shoulder.  I couldn't read his expression with his mask in the way.



I sighed and confessed, ``I'm\ldots I guess I'm waiting for the other shoe to drop.  Isn't that what happens?  The second things start to go right, the next disaster strikes?  Empire Eighty-Eight, Leviathan, The Nine, Dragon\ldots''



``That's a pretty defeatist way of thinking,'' Trickster commented.  ``Didn't Tattletale basically say that there's nobody left to cause us any problems?''



``There's always something,'' I said.  ``I'd rather anticipate it and be ready.''



``Look at it this way,'' Genesis spoke.  She was in a human-ish form, not unlike her real self, though she was wheelchair-free.  ``If it's more dangerous than Leviathan, the Nine or the Dragon suits, there's no way we can make some plan to deal with them until they make the first move.  If they're \emph{less} dangerous, we can deal.  Relax.  We're in good shape.''



I shrugged.



``Sooo,'' Imp drew out the word, ``Party?''



``No,'' Grue and I spoke at the same time.  Imp groaned.



``Coil told us to check on our territories.  We should do that,'' I said.  ``Take your costumes off, take it easy.  I'm going to see if the food and drink I'd arranged to go to people in my territory is still okay, and make sure that they get fed and don't have cause to lynch me.  Then I'm probably going to sleep for twelve straight hours.''



``Wait, didn't you just say no party?'' Imp asked.



``It's not a party.  It's something I was doing before the Dragon suits came.''



``Do the \emph{heroes} know that?''



``Dragon could confirm it,'' I said.  ``She disrupted the preparations.''



``Dunno, that sounds pretty flimsy,'' Imp said, sounding way too pleased with herself, ``Maybe you better cancel, just to be safe.''



``Imp,'' Grue growled the word.



Imp laughed, ``I'll go patrol our territory.  I'll be using my power, so no worries about being seen in costume.''



``Coil said we shouldn't go out in costume \emph{at all},'' I said.  ``I thought that part of the message was pretty clear.''



``Fine,'' Imp said.  ``Whatever.  If I'm not supposed to do \emph{anything, }I'm going back to our place, gonna to kick back and catch up on some shitty reality shows.''



``No TV,'' Grue said.



``Nuh uh.  No way.  If you two want to play hardass mom and dad and be controlling assholes, okay.  But you can't tell me I can't watch T.V.''



``I mean you won't get any channels.  There's no cable, no digital connection and no satellite.  Only static.''



Imp groaned, an agonized sound one might expect from someone who had just been speared through the gut.



What did it say about me that my metaphors were tending towards that kind of violent imagery?



``Why don't you come by?'' Regent asked her, ``Play video games?  I've got shows on DVD.  No shitty reality shows, but stuff.''



I looked Grue's way to gauge his reaction to Imp and Regent hanging out, only for our eyes to meet, so to speak.  We were thinking the same thing.



``I don't think-'' Grue started to speak.



Imp wheeled on him, jabbing a finger in his direction, ``Enough!  You don't dictate how I live my life!''



``No fighting, please,'' Sundancer said, from the sidelines, ``We've been through too much already.''



Grue stepped forward, raising one hand, but Imp didn't give him a chance to touch her, backing away, swinging one hand through the air, as if to swat his hand away if he tried.  ``You've said enough!  You don't want me to celebrate my first legit win where I was actually fucking useful?  Fine!  Don't want me to go on patrol?  Fine!  I'll accept that shit because I'll take orders from the guy who actually pays me.  But if \emph{you're} going to whine because I want to play video games with a teammate, I'm not going to stand here and listen to it!  Deal!''



``If you'd just-'' Grue started.  He stopped and sighed.



``What?'' I asked.



``I was going to say something,'' he said, turning around.  ``But I can't remember what.''



We experienced a moment where the conversation died, where nobody was sure what to say next, and nobody was able to tie things back to the prior conversation to resume an earlier topic.



``We did what we were supposed to do,'' Trickster said, finally.  ``Good work.  Skitter's right.  Let's go retreat, tend to any wounds, and we'll take a breather.''



There were nods and murmurs of assent from everyone present, myself included.



More to his team than the rest of us, Trickster said, ``I'm located closest to Coil, so I'm stopping by, going to check on Noelle, see if Tattletale needs help setting our captive Director free, and then I'll talk to Coil about his progress with \emph{our} issues.''



``Don't get on his case,'' Genesis said.  ``Whatever his plan is, he's under a lot of pressure right now.  I'd rather wait another few days and then talk about it with him than push it now and risk upsetting him.''



``The difference between us,'' Trickster said, terse, ``is I'm not willing to wait.''



With that said, he tipped his hat at me and walked away.  He wasn't three paces out the door before he found something to swap with, leaving a mailbox at the mall's edge.  The rest of the Travelers began to file off.



``I'll be off too,'' Regent said.  He offered me a sloppy mock-salute, ``Good work, chief.''



I winced at that.  I hadn't wanted to raise the subject of me taking over as leader for the previous confrontation.  I glanced at Grue and found him looking at me.



``Can we talk?'' he asked.  \emph{Thanks, Regent}.



``Yeah,'' I said.



``We did make plans.''



``You're dating?''  Bitch asked.



``I didn't say that,'' Grue said.



``But you're dating.''



``Yeah,'' he admitted.  Bitch looked at me to double check and I nodded.



``Hm.''  She somehow conveyed smugness with the monosyllablic response.



``You want to come?'' I asked her.  ``Hang out?''



``Nah.''



``You sure?'' I asked.  ``You're welcome to spend some time with us, kick back, watch something, eat some good food?''



``Being around people's too tiring.  Warm night like this, nice weather, figure I'll go play with my dogs.  Make sure they aren't too hurt, throw a few balls for 'em in the moonlight, eat when I want to eat, sleep when I feel like sleeping, not having to worry about getting in anyone's way.''



``You wouldn't be getting in the way,'' I assured her.



``It's all good.  I'm happiest doing this.''



``Well, stay in touch.  If you feel like some company, come by again?''



She shrugged and turned to leave, Bentley to her right and Bastard to her left.  With every step Bentley was taking, he was getting larger.  When she was nearly out of sight, Bentley was big enough for her to climb on top of.



Leaving Grue and me standing in the mall.



``I'd almost think you didn't want to spend time alone with me,'' he commented.



He was looking at me.  I felt scrutinized, like every movement and every part of me was suddenly under the spotlight, anything I did potentially being read as meaning something.



``No,'' I said, very carefully.  \emph{Not exactly. } I just didn't want to hurt him by taking away his role on the team, and I \emph{knew} it would come up\emph{.  }I tucked my hair behind the spot where the armor of my mask covered my ear.  ``No.  Being alone together is good.''



``Your place?'' he asked.



``Yeah.''



\sectionbreak



My people were active in my territory, but they were busier cleaning up the mess than they were actually getting stuff done.  It was irritating on a lot of levels.  We'd been \emph{accomplishing something}, and Dragon had interrupted.  \emph{We're in the world on the other side of the looking glass}, I thought, \emph{where it's the heroes who get in the way of progress and recovery}.



I could understand why Dragon did it.  I wasn't saying it was her fault, exactly.  Especially if it wasn't actually her directing the suits.  But it was still irritating.



The silence between us was a tense one.  I wished Bitch had decided to come along.  Not because it would have generated conversation, but because it would have put off the subject of discussing team leadership, and the third wheel would have made for a reason for the quiet.  Was it bad of me to think about using her like that?  Or was it just accepting that she made an uncomfortable silence comfortable by her very nature?



I used my power to scout for any groups of people as we made our way to the beach.  We weren't supposed to be out in costume, but we didn't have any great options at this point.  I figured Coil would forgive us this much.  We entered the storm drain and made our way up to my lair.



Charlotte and Sierra looked surprised to see us as I opened the door.  Charlotte had three kids sitting on the couch with her, while Sierra reclined.  She rose to a sitting position.



``What happened?'' Sierra asked.  She glanced nervously at Grue.



I saw Charlotte and the kids had plates on their laps.  The pork we'd been cooking earlier in the day.  I headed for the fridge and found a hunk of it wrapped in cling film.  ``The PRT didn't like the fact that we'd claimed control over Brockton Bay, so they sent in seven Dragon suits to root us out.''



``What do you want us to do?'' She asked.



``Nothing.  It's fine.  Stick to business as usual.  I'm glad you managed to get back to the food in time to make sure it finished cooking alright.  Any other problems?''



``We didn't get a lot of work done,'' Charlotte said.



``We weren't going to anyways,'' I said, ``That's fine.  I'm going to grab some food.  Grue, you want any?''



``Yeah.  Please.''



``Seven Dragon suits?'' Sierra said.  ``If they come back-``



``They're dealt with,'' Grue said.  Was the surprise on Sierra and Charlotte's faces because of what Grue had said, or was it the way he'd said it with such confidence in his strange, echoey voice?



I set two servings worth of the pork onto one plate and put it in the microwave.  ``They may come back, but that'll be a little while coming.  What I'm worried about is my territory.  Were people upset?''



``Yeah,'' Sierra said.  ``A few people got shocked by those floating flying saucer things.''



``The drones,'' I said.  My heart sank a little.  My promise to protect my people had been broken yet again.



``Yeah.  Drones.  People were pissed.  They were trying to get the drones, catch them in trash cans, but the wings got in the way, so they started using tarps.  They even got hold of a few before the drones started fighting back.''



Grue gave me a look that I couldn't read.  Stupid masks.



``Anyone seriously hurt?''



Sierra shook her head.



``Ok, good.  Listen, I'm going to be working from the background these next few days.  I won't be appearing anywhere in costume or overtly using my powers.  Are you okay with keeping things running smoothly?  I'll be available by phone if you run into any problems.''



``I, um, I don't know.''



I opened the microwave and withdrew the plate of smoking, herb-rubbed pork.  ``What's the problem?''



``I'm worried people are going to recognize me, and it'll get around to the people I know.''



``I'm not asking you to do anything criminal.  I'm just looking for someone I can trust enough to put in a management role.  Make sure things are cleaned up and that nobody's slacking off.  It's nothing you wouldn't be doing working for a cleanup crew somewhere else in the city.''



``Except I'm doing it for \emph{you}.  I'm working for a criminal.  Even doing what I'm doing right now, it doesn't sit right.  No offense.''



``Okay,'' I said, pausing.  I was apparently taking too long to prepare the food, because Grue was edging in to take over the preparation, cutting the meat into two portions and arranging the plates.  How was I supposed to manage this?  ``Listen, I'll take five thousand dollars out of the safe upstairs, sometime late tonight or early tomorrow.''



``It's not about the money, or the lack of money, or any of that-'' she protested.



``I know.  I'm not trying to bribe you.  Not exactly.  I guess, um\ldots'' I trailed off.  I was tired, thinking at high intensity for too much of the day.  ``Um, I'm trying to say I trust you, and I value the work you put in.  So take that money, then if you know of someone who could do what I'm asking, someone like Charlotte or someone else you think we could trust, give them as much as you think is appropriate.  If there's any left over, maybe you and Charlotte split it.  Or split an amount between the people who fought the drones, and be sure to tell them that as much as I appreciate them standing up to Dragon, I \emph{don't} want them to do anything like that again.''



``You don't?''



``The last thing I want is people who live in my territory to get hurt for my sake.  And I don't want you to be inconvenienced either.  Think about what you'll do with the money tonight.  But don't overthink it.  It's a gift, a thank you.''



``I can't take your money,'' Sierra said.



``Then don't,'' I told her, trying to look like I was more focused on the food than anything else.  It wouldn't do for her to see how much this was gutting me, and I didn't want her to get guilted into anything.  I grabbed a coke from the fridge.  I gestured with it to Grue, and he nodded.  I grabbed another for him.  I had to swallow and clear my throat before I said, ``I hope you'll stay.  I really do.  But if you're not comfortable doing what you're doing, that's okay too.  You can take a secondary role, or you can leave.  I'll be disappointed, but I won't be angry.''



``Okay.''



I looked at Charlotte and the kids, the steaming plate in my hand, a coke in the other, my right foot resting on the bottom stair of the staircase.  I asked Charlotte, ``Are \emph{you} okay with the status quo?''



``Yeah.  But I'm just looking after the little ones, and making sure people get fed.  I'm out of sight, I don't come off like a second in command or anything.  I- Sierra and I have talked about this, before, her being uncomfortable.  I'm okay because this works for right now, but I understand what she's saying?''  Her voice quirked with uncertainty as she finished speaking, as if she were asking a question, or asking permission to have that opinion.



``I understand too,'' I said, sighing.  ``I'm sorry I haven't been around enough for you to talk to me about this, Sierra.''



``You've had bigger things to worry about.''



``And I shouldn't have forgotten about this stuff while I was doing it.  I'm sorry.  You do what you need to do, decide if there's any compromises or options you want to ask for.  I think I'll understand, whatever you do.''



She nodded.



Grue had walked ahead of me and stopped halfway up the stairs.  I followed him, leaving my nanny-cook and reluctant lieutenant behind.



\emph{Fuck, fuck, fuck}.



``You going to work that out?'' Grue asked.  He paused on the second floor.  After a moment's thought, I tilted my head up toward the next set of stairs.



``Don't know.  Hope I can keep her.  Wouldn't have made it this far without her to hold things together when I was away.  If there was something I could do for her, maybe I would.  I dunno.''



We stepped into my bedroom.  I was glad I'd left it more or less tidy, but I had to take a second to hastily make my bed and throw some stray clothes in the hamper.  I moved some folded clothes from a wooden chair and let Grue take the seat.  I grabbed a remote and turned on the TV, only to remember that there wouldn't be anything to watch.  I left it on the display screen for the DVD player.



Edgy with nervous energy, I took a moment to remove my mask and find a pair of glasses from the bedside table before seating myself on the edge of my mattress, my soda at my feet.



Grue had pulled off his helmet in the meantime to start eating, and I saw his face for the first time since we'd left his apartment for Coil's.  I could see the dark circles under his eyes, which suggested he probably hadn't slept well last night.  He wasn't better, but it wouldn't be reasonable to expect him to be.



Brian swallowed, ``I wish I could offer you advice, but Imp and I are at a point where it'd be \emph{nice} if we had to worry about retaining\ldots what did you call them, way back when?''



``Employees.''



``Right.  If we had to worry about keeping our employees, it'd be good, because it'd mean we actually had some.  I'm not sure how to get underway on that front.  We're intimidating.''



``I'm intimidating,'' I said, admittedly defensive.



``You are.  But I'd say you're more intimidating as an \emph{idea }than you are in person.''



``Gee, thanks.''



``No.  That's not bad.  You're more intimidating overall than I am, and yet you're more approachable than I am.  I'm tall, I've got broad shoulders, I've got the mask, I've got the mass of darkness rolling off me.  People run when they see me coming for them.''



``My costume isn't exactly lovey-dovey, either.  I've got the bugs crawling on me.  Sure, I'm smaller, narrower, but-``



``The idea of being attacked by you might be spooky, but even if you can hold your own most of the time, people don't imagine getting in a hand to hand fight with you and feel scared.  It's your \emph{power} that's scary.  Me?  I think people look at me and they can imagine me pounding them into a bloody pulp, or worse.  My power's inconvenient, it's spooky, but it's not the scary thing.''



``You can't really see your darkness, though.''



He shook his head, ``I know where it is, but I don't really see it.''



``I think you underestimate what it's like.''



``Maybe.  But my point is that people are more likely to run than stick around and talk when I'm approaching.  You can take your bugs off the table, make it clear they aren't a threat, and people feel less threatened, they're willing to hear you out.''



``Maybe.  But if that's the case, don't give them a chance to run.''



``What?  Pop out from around a corner, scare the living daylights out of them, then offer them a job?''



``Sure.  Why the hell not?  Or have Imp break into apartments and leave a card.''



``I don't think that would send the right message.  It's vaguely threatening.''



``\emph{You're} vaguely threatening.  If your prospective hires can't deal with that much, then they probably won't handle the job all that well, either.  If you can't find anyone, then maybe I send some of my people your way to help get you started, or you could shell out for some decent mercenaries.''



``Maybe.''



``There's options.  Don't stress about it.  Whatever else happens, we have a few days before we decide on the next leg of our plan.  Let's relax.  Movie?''



``Sure.''



I stood from my bed and began going through the box of DVDs that Coil had supplied with the TV.  Most were still in the tight plastic wrap that they'd been bought in.  I looked through, then handed some to Brian before turning back to the bag to keep browsing.



What the hell were we supposed to watch?  I didn't want anything that would ruin Brian's mood or remind him what had happened, so horror was probably out, I was sick of the high intensity stuff, but I couldn't stand romance or bad comedies.



``Going back to the earlier topic,'' Brian said, ``The subject of leadership, being in charge\ldots''



I winced.



``You took over today.  Are you wanting that to be a permanent thing?''



I turned around.  ``No.  Not permanent.  Just until-'' I stopped short.  How to put it?



``Until?''



``When I was getting really obsessive about what I was doing, when I was losing sleep and making mistakes, I deferred control.''



``To Trickster,'' Brian said.  I could see a shadow pass over his expression.



``Yeah.  And that's a bad example because it didn't work.  It's just that we both know you're not getting enough rest.  So maybe I can pick up the slack in the meantime.''



Brian sighed.  He didn't look any happier.



``I don't want to make you unhappy,'' I said.  ``I'm not wanting to oust you, or co-opt your role permanently or completely.  You were the leader, even if we didn't really establish an official title over it.  But we can divide the duties for the time being.  Tattletale handles the information angle of things, I maybe keep Bitch reined in and handle the spur of the moment calls, while you handle Regent and Imp and all the rest.''



``Which is less than it sounds like, especially when you and Tattletale contribute on `the rest' in little ways.''



``No-'' I started, then I sighed.  ``Maybe, yeah.  I don't want to come off as manipulative or anything.  Like I said, I don't want you to be unhappy, but at the same time I do want the whole team to get by in the meantime.''



``You don't sound manipulative,'' he said.  His fork hit the plate with a clatter.  ``Jesus, this sucks.  I know you're right.  I know this is for the good of the team, and if I could just get over this shit-``



``It's not that easy.  Don't do yourself a disservice and expect too much.''



``My whole life, I've been bigger than my peers, I've been stronger than most.  Spent my time around pretty powerful guys.  Boxers, martial artists, other criminals.  I didn't have many \emph{friends}, but they were the people who were around me, you know?  And they were the types to go after you if you show any weakness.''



``You get shot, nobody's going to call you a wimp.  I don't see why it's different if the damage is mental or emotional instead of physical.''



``I know, but you're not getting it.  \emph{I} was the type to go after someone if they showed a vulnerability.  Wasn't until I'd had my powers about a year, Aisha tells me I was being an asshole, just like one of her stepdads used to be.  So I tried to be better, but I always wanted to protect her, always wanted to help others.  Teach you and Alec to fight, step up and take charge when a situation demanded it.  Sometimes when a situation didn't.''



``Yeah.''



``So it isn't just about me trying to adjust.  Christ, it's me having my world turned upside down.  It's others protecting me, others helping me, others covering me in a fight, others taking charge.  Aisha's the one fixing things for me.  And you-``



``Me?''



``This thing with Coil.  Don't think I'm so obsessed with what's going on with me that I don't see it.  It's like a burden's fallen from your shoulders.  You've got \emph{concerns}, but you're more relaxed.  You've got hope that you didn't have twelve hours ago, and it's dramatic enough that your posture's changing.  Even since we left the mall, it's like you're slowly convincing yourself that this is over, Coil's going to follow through, we'll move on to taking care of our territories and everything works out in the end.''



I folded my arms.  ``I don't think that.  Like I said, I'm waiting for the other shoe to drop.''



``You \emph{say} that, you tell yourself that, but I don't know that you're feeling it.  I'm worried you're setting yourself up for a massive disappointment, and that you'll be affected enough that you won't be able to deal when it happens.  But I'm mostly worried that all that will happen and I won't be in a position to help because I'm distracted by my own shit.''



``You don't have to take up all the slack.  We have other teammates.''



``Lisa isn't exactly a heavy hitter, and let's not fool ourselves into believing that Alec, Rachel or Aisha are going to offer any meaningful emotional support.''



``We'll manage,'' I said.  ``We've managed this far.''



``More or less.  Problem is, `managing' is fine, up until we \emph{don't} manage, if that makes any sense.  Then it's over.''



I sighed.  ``How did Genesis put it?  There's no use in getting worked up over it if we can't plan around it or do anything to change it.  So we'll each do our own imperfect jobs of taking care of each other and taking care of ourselves, and be as ready as we can for whatever comes up.''



He sighed.



``We're not perfect.  We're flawed people, and as much as I want to help you in every way I can, I know I can't.  I don't- I'm not good at this.  I don't know how to act, or what to say.  But I like you.  I care about you.  I'm going to do my best, even if I know it's not good enough.  And I won't expect any more of you.''



He nodded, but he looked glum.



``No hard feelings?''



He shook his head.  He didn't look happy.



``I won't be leader forever.''



``I don't know,'' he said.  ``Might be better that you keep the job, even if I do bounce back eventually.''



``Except I don't \emph{want} the job.''



``That might be why you should take it.  I don't know.  Can we drop the subject?''



``Sorry.''



``It's okay.  Just\ldots heavy topics, with lots of ramifications.  And it's hard to shake the negative thoughts.  I'd rather talk along the lines of what you said before, about taking care of each other.''



``And taking care of \emph{ourselves},'' I said.  ``Getting enough sleep, eating right.''



``Okay,'' he said.  There was a pause.  ``I slept well the other night.''



``Then stay over.  There's nothing pressing coming up, so we'll watch movies until we fall asleep.''



He smiled a little, and for the first time in a long time there was a glimmer of that expression that had gotten my attention in the first place.



I put three DVDs into the drive so I could use the remote to play the next movie without having to get up, then pulled off the armor panels of my costume before settling into bed.  My back pressed against his chest, and I could feel his breath against my hair.



I felt so self conscious that I could barely keep track of what was going on.  I was thinking every unromantic thought there was: worrying if I had body odor from being in costume and running all day, wondering if I should get up to go to the bathroom now so I wouldn't have to go as desperately as I had the other morning.



I felt his hand on the zipper at the back of my costume, lowering it an inch, then stopping.  A fingertip traced from the `v' where the top of my costume parted, all the way up to the the nape of my neck, then back down.  I could feel his fingers on the zipper, felt every tiny hair on my body standing on end.



A million thoughts raced through my head at once.  All put together, they amounted to a mumbled, ``Um.''



There was no response from behind me.  I could hear him breathing, I could feel the warmth of his breath, the slow rise and fall of his chest against my back.  He was waiting for me to make my decision, and the thing that loomed largest in my mind was the sensation of his fingers on the tiny tag of the zipper, strong, insistent, \emph{there}.



Any confidence I'd picked up in the past weeks or months fled.  I felt as vulnerable as I had in early April, brought to tears in front of my worst enemies.  Except this\ldots wasn't wholly negative.  Not entirely: I still felt acutely aware of every vulnerability, I thought of every part of myself that I tried to ignore when I looked in the mirror in the same way I might see my life flash before my eyes before I died.



Again, thinking that way.  Why couldn't I think in a more romantic way at a moment like this?  Was I broken in my own way?



``Let me get up and turn off the lights?'' I asked.



His power blanketed the room.  I could feel the phantom touches of it on against the thin fabric of my costume and my bare face, leaving me blind and deaf as we were plunged into darkness.



As \emph{I }was plunged into darkness; he could see just as well.  This totally wasn't what I'd wanted.



``That's not fair,'' I murmured.



He placed one hand on the side of my head to get me to turn his way, then pressed his lips against mine.



I didn't protest any further.





