





Living in a city meant dealing with some recurring issues.  Crime, having to lock the doors, congestion on the roads, crowds getting in the way on footpaths; stuff we dealt with so often that we considered it routine.  We considered it background noise or we managed without even thinking about it.  Construction work was something we couldn't dismiss so readily, something that always seemed to elicit groans and complaints.  Maybe because it was so blatant, so grating, and it changed in tone, location and degree often enough that we couldn't adjust.



Not today.



No, I felt a level of satisfaction and security as the bulldozers and piledrivers went to work in my territory.  For every car on the road, there were ten trucks carrying debris out and five trucks bringing materials in.



A lot of that would be Coil's doing, I knew.  There was construction and clearing going on throughout my territory and building inspectors were checking blocks, all despite the warnings that were going around regarding big, bad, unpredictable Skitter, and that would be because he greased palms or the construction companies at work were \emph{his}.



Damn it, I felt restless.  I wanted to go to Coil's territory and discuss Dinah, and I might have, if Trickster hadn't been the first to speak up and declare he was going to confront Coil.  I suspected that Coil wouldn't release Dinah this soon, and if he was under too much pressure to hear Trickster out, he certainly wouldn't listen to me.  If he \emph{did} have something to offer Trickster, he wouldn't welcome my distraction.  I had to wait.  I hated it, but I recognized it as the sensible route.



Trickster's focus was on Noelle, though, and nothing I'd seen indicated that Coil had made any advances on that front.  All I knew, really, was what Tattletale had told me and the little things that had come up in our brief discussion with the Travelers about our strategy.  She'd been a girl, maybe not in the best of health.



It was possible Trickster had been trying to save Noelle in the same way I was trying to save Dinah.  The circumstances were different, obviously: Coil was the best answer the Travelers had to Noelle's situation, but he was the cause of Dinah's.



Still, it made me think.



I was officially hands-off in my territory.  I wasn't going to deviate from orders \emph{now} and risk upsetting Coil.  That meant no costume, no showing my face, no intervention in the management of things.



Which turned my thoughts to Sierra.  As far as my ability to sense things with my swarm went, Sierra was easier to identify than many.  Her dreads gave her a distinct profile.



I couldn't find her.



I \emph{could} find Charlotte.  That wasn't a problem; she was in the company of the kids, half a block away, giving each kid two six-packs of plastic water bottles to ferry out to the various work sites.



``You've been lying there since I woke up, eyes half-open, staring off into space.''



I blinked hard, then rubbed my eyes.  ``Hey.''



``Hey.''



I looked at Brian.  He was pulling himself up to a sitting position, the covers over his lap.  I glanced over his upper body.  None of the battle wounds I'd seen him sustain in the past were there anymore.  The scars from the shallow cuts Cricket had carved into his chest were gone, as were the defensive wounds and old scars on his hands and arms.  He was in perfect shape, physically.  Physically.



But I'd sort of explored enough to discover that last night.  It hadn't been a perfect night, not even excellent, but it had been nice.  Considering all of the other humiliating or awkward possibilities, I was happy to take nice.



Thinking about it made me self conscious.  I pulled the sheets up to my collarbone.  ``You sleep any?''



``Some.  Woke up in the middle of the night, I made some noise.  I'm surprised I didn't wake you.''



I frowned.  ``You should have.''



He shook his head.  ``You were exhausted.  Once I saw you there, it helped me to realize where I was, dismiss them for the dreams they were.  Took me a bit to relax, but it wasn't \emph{bad}.  Being here.''



Hated that, that he was struggling like that and I couldn't help fix it.



``Do you need to talk to someone?  A psychiatrist?''



I could see him flinch at that, his entire upper body stiffening in some kind of knee jerk resistance.



I waited, not pushing.



He sighed, and I watched that battle-readiness slowly seep from him, the tension leaving him.  Up to a point.  ``Don't we all?''



``Probably.  But you're the one I'm worried about.''



``I'll figure this out myself.  Have to do this myself, or I feel like it won't count, it won't really be a fix.''



I didn't like that response, but it was a hard one to argue with.



``I won't pester you about it.  But can you at least tell me that if this goes on for any length of time, you'll go get help?''



``It'll get better.  Has to.  I feel like I've taken strides forward, forcing myself to let down my guard, to be here with you.''



I tensed, ``Forcing yourself?''



``That's not what I mean.  I mean, you know.  I\ldots I can't relax.  Can't stay still, can't stop watching over my shoulder or make my brain stop replaying scenes in my head.  Except I can, if I'm active, if I'm doing something like we were against those Dragon suits, or if I'm with you, and I'm lying here in your bed, trying not to wake you up.  Then I know I can't get worked up, it gives me these boundaries I can force myself to work inside.''



My eyebrows drew together in concern.  ``It sounds like it's causing you more stress in the long run.''



``No,'' he said.  He reached out and used both of his hands to seize mine.  He squeezed.  ``Come on, no.  Is that really what you want to talk about right now?''



``I'd love to talk about other stuff,'' I said.  I wasn't sure I was telling the truth.  Things were more awkward in the light of day.  Only seconds ago, I had prodded a sore spot for him by raising the idea of psychiatric help.  Offended him.  If I didn't clear my head and get centered, I wasn't sure I trusted my ability to avoid another misstep.



``But?''



``But I made plans with my dad.  It's\ldots''  I paused, closing my eyes, ``Nine-twenty-eight.  I figure I need to shower and get dressed, which might take an hour, eat, do a quick walk around my territory in civilian clothes, then head over.  I want to spend time with you, but after the intensity of the past little while, taking things slow this morning feels like a nice idea.''



``How do you know the time?''



``Bugs on clock hands,'' I said, pointing toward my bathroom.



``Ah.  You want company?''



My eyes widened a little.  ``In the bathroom?''



He grinned.  ``For breakfast.  And the walk-around, if you want.  I could learn stuff.  We're liable to lose track of time if we share a shower.''



``Yeah,'' I said.  ``Please, we'll have breakfast, walk.''



I climbed out of bed, tugging one of the sheets free of the bed so I had something to wrap around myself as I made my way to the bathroom.



With my bugs, I could sense Brian getting out of bed shortly after I'd abandoned the sheet, climbed into the shower and pulled the makeshift shower curtain into position.  He made his way downstairs and began putting breakfast together.  He set two plates down, and then said something to the empty room.



I still had the scene in mind a little while later, as I ventured downstairs.  I was dressed now, a tank top, jeans and sweatshirt around my waist, my hair towel dried but still damp.  ``Were you talking to me?''



``I was saying it probably isn't very hygienic to have houseflies landing on dinner plates.''



Ok, so he wasn't going crazy.



``They landed on the edge, and they're mine.  From the terrariums upstairs.  They're in as sterile an environment as you'll get.''



``Okay.  Just saying.''



``I can't hear you through my bugs, by the way.  It's not the first time you've done that.''



``Right.  Wasn't sure, because Tattletale said you were working on it.''



I shook my head, ``No progress.''



``And I'm getting used to talking to empty rooms.  Sometimes catch Aisha off guard.  Breakfast?  Sit down, I'll put the kettle on.  Didn't want to fill it while you were in the shower.''



``Thank you.''



Through some unspoken agreement, we didn't talk about `work'.  We didn't discuss Coil, Dinah, the Travelers, Dragon or the Nine.  Instead, our discussions turned to favorite movies and shows, my favorite books and memories from our childhoods.  Shows we'd watched and nearly forgotten, moments from school.



Emma came up a lot, as I thought back on it.  My parents too.  The three of them had been the focus of my world, with everything else taking a distant second place.  Emma had turned on me, my mom had left me, and my dad\ldots I had to admit I'd left him.



I didn't raise any of the heavier stuff, but I mentioned that Emma had turned out to be one of the bullies that plagued me throughout my stay in high school.



Brian, in turn, talked about his life growing up.  That \emph{did} touch on the heavier stuff, and as much as I liked learning a bit more about the details of his life, I was glad when we detoured into a discussion of martial arts.  As he explained it, he was more interested in the broader strokes and philosophy of a given style than on the particulars.  Once he had a sense of how a given adherent of the style might approach a fight and enough basic techniques to see how they put it into practice, he tended to lose interest.



All around us, I could see people hard at work.  My people were deferring to any legitimate construction crew that set to work, shifting their focus to nearby areas.  I could see people moving supplies out of a nearby building so the crews could bulldoze it, others helping to unload a truck of building supplies.  When I got back to this and started to give orders, I'd have to find work for them that wouldn't put them in the way.  I couldn't quite track how many people were working for me in my territory, but it was far more than before.



I felt like I should be \emph{losing} people each time I got pulled into a fight against a major threat.  I \emph{had}, when Mannequin and Burnscar had attacked, but I'd walked away from the first Mannequin fight with something of a following, and I'd expected to see my people leaving in droves after Dragon made her move.  Except it wasn't happening, and I wasn't entirely sure why.



Our walk took us on a circuit, with us turning back to my lair, and I left to go back to my dad's while Brian headed back to my place to use the shower.



I felt weird about that.  Parting ways so casually after spending the night together.  Oddly enough, I felt weird about letting him in my lair while I wasn't there.  He'd be passing through my room, seeing my stuff.  I knew it was paradoxical to be bashful, covering myself with a sheet and feeling guarded about my privacy, all things considered, but that didn't change the fact that I felt that way.  I wouldn't refuse to let him use my bathroom because of it, but yeah.



In a way, we'd sort of done everything backward.  We'd started with the long-running partnership.  With the `family', if I wanted to think about managing the others in that sense. In the course of that, we'd been through hell and back, we'd backed each other up, helped each other.  All hurdles one might face in a marriage.  Then there were the more recent cases of actually talking about the relationship happening, there was last night, then the more casual date and getting to know each other better this morning.  If it wasn't a hundred percent backwards, it was at least pretty jumbled up.



Or maybe I was looking at it in an immature way, expecting some simplistic, formulaic, storybook notion of how a relationship was supposed to proceed.



I made my way to my dad's, thinking about a thousand things at once, not wanting to think about anything in particular.



There were cars parked out front.  There was a strange car in the garage with the door open, two others in the driveway, my dad's at the end.  With a few stray houseflies, I casually noted a dozen people inside the house.  My dad was there, too.



I immediately thought of Coil.  Had he divined what I had planned today?  Planned some counterattack?



I'd foregone my costume, so I wouldn't feel compelled to use it in a pinch, and I'd removed my knife holster from the costume and had it clipped to the back of my waistband, so it was in the midst of the folds, blanketed by various wasps and spiders.  The setup might have been awkward for anyone else, but spending the past few weeks and months while using my bugs to help guide my hand left me fairly confident that I could slip my hand through the folds and draw it at a moment's notice if I had to.



Then a man opened the door.  I let myself relax.



``No shit,'' he said.  ``Taylor?''



``Hi, Kurt,'' I greeted my dad's coworker and longtime friend.



``Been a long time.  Barely recognize you, kid.''



I shrugged.  ``How're you doing?''



He cracked a wide grin.  ``Working.  Getting by.  Better than we were doing.  Now, you coming inside or are you going to stand in the driveway for the next five minutes?''



I followed him into the house.



My dad was in the living room, surrounded by familiar faces.  People I'd seen around when I'd gone to his workplace or when they'd dropped by the house.  I could only put a name to the people who my dad called friends: Kurt, Kurt's wife Lacey, and Alexander.  Even Lacey was burlier than my dad, with a build like Rachel's, muscle added onto that.  The other three were familiar, but I didn't know them well.  My dad and myself excepted, every person in the house had spent their lives doing manual labor.  Just looking at him, he looked like the odd one out in every way, in clothes and body type and demeanor, but he was relaxed in a way I hadn't seen in years, surrounded by friends with a beer in hand.



My dad saw me, mouthed the word `sorry'.



Kurt saw it.  ``Don't blame your old man.  Alexander brought a truckload of beer in from out of town, we got to drinking.  We thought we'd include Danny, drag him along, invited ourselves.  Didn't know he had plans.''



``It's fine,'' I said.  Nobody that could be a threat, none of Coil's people.  I let myself relax.  What had I been thinking?  That he'd strongarm my dad?



``Heya Taylor,'' Lacey said.  ``Haven't seen you since the funeral.''



Nearly two years after the fact, it still hit me like a punch in the gut.



``Hell, Lacey,'' Kurt said.  ``Give the girl a second to get used to having people in her house before you drop that on her.''



I glanced at my dad, elbows on his knees, a 24 ounce beer clasped in both hands.  He'd lowered his head to stare at the can.  He didn't look devastated, or even unhappy.  It hadn't caught him off guard like it had hit me.  Knowing these guys, I could guess it came up with enough regularity that he was used to it.



``Ah, baby,'' Lacey said.  She raised a beer in my direction.  ``Just a little drunk.  Wanted to say, your mom was good peoples.  She hasn't been forgotten.  Sorry if that came out a little direct.''



``S'okay,'' I replied.  I shifted my feet restlessly.  I'd never felt more a stranger in my own house.  Didn't know where to go, where I wouldn't be drawing attention, have people asking me questions.  It was hard enough with my dad and I having this distance between us, but there were other people in the equation now.



Kurt spoke up, ``We're leaving in a few minutes.  It's hard to get around, so they're scheduling events together so we don't need to make two trips.  The last debate is this afternoon, then mayoral vote right after.  You catch the debate the other night?''



I shook my head.  ``Didn't even know it happened.''



``Well, if that's any indication, this one's bound to be a pisser.  So we're drinking to mellow out.  And I'd feel a hell of a lot better if your \emph{dad} had more than the one beer, so he can relax some and hold back from choking one of the smarmy bastards.''



``Not about to do that,'' my dad said.



``Wish you could.  But it wouldn't be worth it in the end if you wound up in jail and left that daughter of yours alone.  It's all good.  We'll go in stinking of beer, offer some drunken commentary from the sidelines, punctuated by a few off-color words,'' Kurt smiled.



``Please don't,'' my dad said.  He hadn't raised his eyes from the beer in his hands, but he was smiling, too.



``You want to sit and let 'em say what sounds good for them?''  Kurt asked.



``I was thinking it'd be better to ask the hard questions, if we get a chance.  A big part of the crowd's going to be people from the north end.  Good few of them are going to be from the Docks.  So why don't we ask him what's happening with the ferry?''



``He's going to brush it off,'' Lacey said, ``Not in the budget, with everything that's going on.''



``Then \emph{that's} a good time for some booing and drunken swearing,'' my dad answered, smiling.



Kurt busted out a laugh.  ``You want to start a riot, Danny?''



``No.  But might sway the undecideds to see just how unimpressed we are with the man.''



``\emph{Everyone's} unimpressed with Mayor Christner,'' Alexander spoke up.  He was a younger guy, heavily tattooed, with thick eyebrows that gave him a perpetual glower.  Every time I saw him, he had his hair cut in a wild style.  Today he had the left one-third of his head shaved, showing off a fresh tattoo of an old-school pinup girl in a bikini with her elbow appearing to rest on his ear.



``Disaster does that.'' I spoke up.  ``We want someone to blame, and the guy in charge makes for an easy target.''



``He's a \emph{deserving} target,'' Kurt said, seating himself on the arm of the chair Lacey was in.  She wrapped one arm around his waist.  He went on, ``There was this thing in Washington.  Talking about whether they should throw walls up around the edge of the city, blockade the streets and shut off services, get everyone out of here.''



``He said no, right?''



``He said no.  Asshole.  Probably earns more money this way.  Take a few million for restoring and helping the city, help himself to a percentage.''



That surprised me.  ``You're not happy the city was saved from being condemned?  Did you \emph{want} to be kicked out of the city?  To leave your home?''



``It'd suck, but the way they were talking about it in the paper, there's a big fund that's set aside for covering the damages those Endbringer motherfuckers cause.  Idea was that they'd dip into those funds, give everyone that they ousted a bit to cover the cost of their homes.''



``There's no way that's doable,'' I said.  ``What about everyone who left when they were told to evacuate?''



``Don't know,'' Kurt said.  ``I'm just saying what the papers did.''



I felt an ugly feeling in my gut.  ``And they'd give us what the houses used to be worth?''



``They'd give us what the houses might be worth \emph{now},'' he said.



``So not much.''



``It's more than they'll be worth a few years down the line, after the rot sets in and any mold problems get worse.  Getting expensive to get supplies into the city, which means it'll be costly to fix things up and renovate.  Not necessarily worth it.''



``I saw construction crews at work.''



Kurt downed a swig of his beer and cleared his throat, ``Sure.  The companies that are buying up all the materials, purchasing land on the cheap, all in the hopes that this city gets its act together and the land turns out to be worth something.''



``It could.''



``\emph{Come on},'' he made the words a groan, ``We're under the tyranny of supervillains.  Heroes don't have what it takes.  Used to be they were outnumbered but they were trying, making a difference in little ways.  Now they're outnumbered and losing.  What's the point?''



``Just a hypothetical question,'' I said, ``But isn't it better to be in a city that \emph{works}, where villains rule the streets, instead of a failed city with the same villains in a less prominent position?''



Lacey groaned a little, ``Sweetie, had a few too many to wrap my head around the question.''



``Might be time to stop then, Lacey,'' my dad said.  Turning to me, he said, ``I suppose you're asking the classic question, Taylor.  Would you rather be a slave in heaven or a free man in hell?''



``Free man in hell,'' Kurt responded.  ``Fuck.  You think I'd be doing what I do, living \emph{here}, if I was willing to make nice, suck up to the guys in charge and do what I was told?''



Some of the others were nodding, Lacey and Alexander included.



I looked at my dad.



``What's your answer, Danny?''  Kurt asked.



``I'd rather not be a slave or in hell,'' my dad responded.  ``But sometimes I worry I'm both.  Maybe we don't get the choice?''



``You're the most depressing asshole of a friend I've got,'' Kurt said, but he said it with a smile.



``Why are you asking, Taylor?''  Lacey asked.



I shrugged.  How much could I say without giving them cause for suspicion?  ``Saw some of the stuff going on in the shelters.  Some sick people, unhappy people.  It was a long while before anything started getting better, and as I understand it, it was the \emph{villains} who made the first move in getting things fixed up.''



``For their own benefit.  You can't rule a hole in the ground,'' Alexander said.



``Maybe,'' I said.  ``Or maybe bad people can do good for the sake of doing good, at least once in a while.  They're taking charge, they're keeping things more or less quiet and peaceful.  It's better than what we had.''



``The problem with that,'' my dad said, ``Is that we'd be setting humanity back by about three thousand years if we let that happen.  It'd be falling back into an iron age mindset and leadership.  The people with the numbers and the weaponry lay claim to an area through sheer military strength.  They stay in charge as long as they can through family lines, merging families with whoever \emph{else} has the military strength.  That lasts until the family in power peters out or someone smarter, stronger or better armed comes in to seize control.  Might not sound so bad, until you figure that sooner or later, the person who gets control is going to be someone like Kaiser.''



``Kaiser's dead,'' Kurt said.



``Yeah?'' my dad raised an eyebrow.  ``Okay, but I was speaking in general terms.  Could just as easily be Lung or Jack Slash, instead of the relatively benign villains that are in charge right now.  Again, I stress, it's just a matter of time.''



\emph{Just a matter of time until we lose -I lose- and someone else claims Brockton bay for themselves, }I thought.



``What would you rather have happen?'' I asked.



``Don't know,'' he said.  ``But I don't think complacency's the answer.''



``Last debate,'' Kurt said, ``People kept bringing up the capes, moderator kept shutting them down, telling them that they were supposed to be talking economy and education.  \emph{Today} we'll hear some talk on the crooks running the city.  Hear what the candidates have to say on the subject.''



``We should go soon,'' Lacey said.  ``If we want to get a seat instead of standing around at the sides.''



My dad looked up at me, ``Can I get you any food, Taylor?  I promised you something.''



``I'm alright.  Had a late breakfast.  Maybe when we get back?''



``I'd offer you a drink,'' Kurt said, chuckling, ``But that'd be against the law.  How old are you, anyways?''



``Fifteen,'' I said.



``Sixteen.''



I turned to look at my dad.



``It's the nineteenth,'' he said.  ``Your birthday was a week ago.''



``Oh.''  I'd been a little distracted at the time.  A week ago, that would have been around the time we were wrapping up our confrontation with the Slaughterhouse Nine.  Lovely.



``That's the saddest goddamn thing I ever heard,'' Kurt said, getting off the chair's armrest and helping Lacey to her feet.  ``Girl missing her birthday like that.  I'm guessing you don't have your license, then, huh?''



``No.''



``Damn.  Was hoping you'd be our designated driver so your dad could have another.''



``I've only had half a tallboy,'' my dad said, shaking his can lightly to let us hear the contents sloshing against the sides.  ``And we'll be driving slow on these streets anyways.  Who's driving the other car?''



Alexander raised his hand.  He only had a glass of water.



``Then we're off.  Out of my house,'' he said.  I could see him wincing in pain as he used the chair's back to help himself to a standing position, but he recovered.  He started shooing the burly dockworkers out the door.  ``Go.  Into the cars.''



We began to file out.  Kurt and Lacey climbed into the back seat of my dad's car.  The others got into Alexander's truck.



``Should you be drinking with the kidney damage?'' I asked, as the doors shut.  ``You had trouble standing.''



``I got cleared yesterday.  I'm back on a regular diet.  Any hurt is just the muscle and the stitches.  Thanks for worrying about me.''



``Of course I'm going to worry about you,'' I said, frowning.



``You \emph{have} changed,'' my dad commented, resting his elbows on the roof of the car.



``Hm?''



``Wasn't so long ago that you would have walked into that situation and clammed up.''



``Feels like that was a year ago.''



``Anyways, I'm sorry,'' he said.  ``I'd hoped this would be just you and me, having a chance to catch up.  They invited themselves.''



``It's okay.  I'm glad that you've got friends like that.''



``They're a bit overbearing,'' my dad said.



``The window's open a crack,'' Kurt said, from inside the car.  ``We can hear you.''



``They're \emph{overbearing},'' my dad repeated himself, raising his voice a notch.  At a normal volume, he finished by saying, ``But they're alright.''



Smiling a little, I climbed into the passenger seat.



``Hey, Taylor?'' Lacey asked.  Her voice was overly gentle, and for a moment I thought she was going to mention my mom again.  I winced a little.



``What?''  I turned around in my seat, as much as I was able with my seatbelt on.



``Just wanted to say thanks.  For the warning.  You told your dad that Shatterbird was around, didn't you?''



I nodded.



``He told us.  We were careful.  I don't know if it saved our lives or not, but thanks for watching out for him, and helping us out as collater- collar--''



``You're welcome,'' I said, before she could fumble over her words any further.



I \emph{was} glad he was in touch with them.  From what I'd seen, I'd been left with worries that my dad was all on his lonesome.  Introverted people like him, like \emph{us}, were best paired with  the Kurts of the world.  Or the Lisas.  People that wouldn't be ignored or shrugged off, people who pushed the boundaries, so to speak, and drew us out of our shells.



I enjoyed the drive as we made our way downtown, more than I thought I would.  My dad and Kurt knew each other well enough that their dialogue flowed easily, and the same went for Lacey and Kurt, what with the pair being married.  I had a feeling that, by the end, Kurt was feeling like he'd wound up on the short end of both exchanges.



The town hall had survived the waves.  The stone building had crenelations and an American flag over the door.  We joined the trail of people who were filing in, walking past stands with the posters and images of the candidates, booklets of brochures about the issues and stands with newspapers from neighboring cities.  My dad and Kurt grabbed a few papers each and put them into the plastic bags that had been made available to us.  It was a nice thought, putting those out.  There wasn't any TV at present and we had to keep abreast of what was going on somehow.



The signs led us past the old historical courthouse and to the auditorium.  We'd expected the seats to be filled, leaving us only with standing room, but the opposite was true.  The back of the auditorium and the rear rows were filled with reporters and camera crews, and the rest of the crowd had filled in random spaces on the benches.  Five or six hundred people.  Somehow less than I'd thought.



It was an odd election, in a way.  The city had been without working computers for a week and a half, most had lost their cell phones, and were left without landlines.  An election without media for advertisement.  For many here, this would be the first and last time they heard a candidate's stances on the issues before voting.  Was this how it had been in the past?  When poorer households hadn't gotten newspapers and there hadn't been televisions or radios?



I looked at the candidates.  A dark haired woman in a dark blue suit, a blond man, and the older incumbent, Mayor Christner.  How many others in this auditorium were aware?  Some time ago, Coil had told us that two of the candidates for office had been bought.  Mayor Christner\ldots well, I could remember standing in his backyard, him pointing a gun at me, pleading for me to step in and save his son's life.



Would the debate turn to the subject of him arguing against the condemnation of the city, and if it did, how would Christner justify the decision he'd made?



I was caught between an ugly feeling of guilt and genuine curiosity in how the event would play out.  Mostly guilt, but I couldn't do anything about that.  I'd done what had to be done.



On the curiosity side of things, I wondered momentarily if either of Coil's mayoral candidates had military backgrounds or if he'd hand-picked his politicians the same way he selected his elite soldiers.



That train of thought ground to a halt as something caught my attention.



It was habit, now, to have my bugs sweeping over my surroundings, giving me a perpetual sense of what was going on in the surrounding three or four city blocks.  When the vans found parking spots around the building, it didn't even warrant a conscious thought.  When the soldiers began filing out of the vans, it startled me.  Men and women with machine guns and body armor.  Not PRT.



No.  Definitely not PRT.



The armored limousine pulled into the middle of the street, just outside the front doors.  By the time Coil climbed out of the vehicle, his soldiers were either just past the doors on either side of the building or standing at the ready to accompany him by the front.



Coil, here?  It didn't make sense.  He wasn't the type to show himself.  It didn't fit how he operated.  Hell, if the mayor was here, his son would be too.  Triumph would be in the crowd.



I glanced at my dad, and he squeezed my hand, ``Not too bored?''



I shook my head, trying to keep my expression placid as my mind raced.



Coil was making his play \emph{right here, right now}.





