





There was a tap on the microphone.  ``If we could have silence from the audience, please?''



The low murmur of conversation throughout the auditorium gradually died down.  The place wasn't full, but four out of every five seats were filled, and there were more people at the back, primarily reporters, many from out of town.



My eye darted across the room, trying to assess the situation.  The heavy woman in the front row, was that Piggot?  It made sense that every person worth talking about would be present.  The disasters and Tattletale's attack on the cell towers meant that there wasn't TV, there weren't phones, and the only way for interested parties to find out what the candidates had to say was actually attending.



Outside of the auditorium, Coil's men gathering in the lobby and at the sides of the building.  Some were taking point on the roof, gathering in pairs, working together to assemble sniper rifles.  Preparing for a fight.  For a war.



Coil was in the lobby, now, and he was joined by others.  I could recognize Circus by the sledgehammer she was carrying, the metal head dragging on the floor.  Coil said something and she lifted it up.  Was he talking about the noise?  It shouldn't matter.  He was accompanied by two others I didn't recognize.  A teenage guy and a larger, more athletic man in a heavy metal frame.



``Thank you to everyone for coming.  Tonight is a three-way debate.  Let me introduce your candidates, starting with Mr. Roy Christner, our mayor incumbent.  We also have Mrs. Carlene Padillo, city councilor of communications; and Mr. Keith Grove, C.E.O. of Eaststar Financial.  Tonight's subjects are crime, public safety and the state of the city.  Would you start us off, Mayor Christner?  What sets you apart from the other candidates in your views?''



I glanced over my shoulder to verify what I was seeing with my bugs.  A young man was making his way up the aisle with a toddler, straight for Coil.



``I won't lie,'' Christner said.  I glanced his way, saw how haggard he looked.  In a way it worked for him, made him look determined.  ``Things are bad.  The situation's improved from where it was weeks ago, but we're still in an ugly situation.  No less than forty percent of the city has evacuated, hospitals are overflowing, and villains claim to own the streets\ldots''



I looked back to the dad and his kid.  They opened the door, stepping through, and two of Coil's soldiers were on them before they could open their mouths and shout a warning.  Putting hands over mouths, the soldiers retreated from the door, separating dad from child.  Within seconds, both were being gagged and restrained.



The door closed on its own, leaving nobody any wiser to what was going on.



``\ldotsinvolved with the defense every step along the way.  I've discussed the subject with Legend, with Dragon and with Chief Director Costa-Brown of the PRT.  Daily, I've been talking with and working with Director Piggot to see what actions need to be taken to see this city restored to what it once was.''



``That's setting the bar pretty damn low,'' Grove said, gripping the sides of his podium.



``No interruptions, please,'' the moderator spoke.  Christner waved her off.  ``You concede the remainder of your turn, Mayor?''



``Let's hear what Grove has to say.''



``Very well.  Mr. Grove.  Two minutes to speak.''



``He wants to restore the city to what it was?  I think he's wanting us to forget that half of our city was a cesspool before the Endbringer came.  Many of you in the audience live in the north end.  You know how bad it was.  Or maybe the Mayor is referring to the city's heyday, when the docks were bustling with activity and the entire city could hear the ships coming in and out of the ports.  If he's trying to convince you we'll return to \emph{that} time, he's telling you an outright falsehood.  The Lord's Port, known to many as the ship graveyard, would cost the city twenty-three million dollars just to clear away the damaged ships and dispose of them.    That's not getting into the cost of actually refurbishing the area and updating it to modern standards.  Or the fact that anyone approaching within a mile and a half of the area is subjected to uncontrollable, suicidal despair.  I visited.  I know.''



I sent a message to Coil, drawing words with my bugs.



`I'm here.  Stop.'



He broke up the words with a casual wave of his hands, scattering the bugs.  Almost dismissive.  Of course he wouldn't stop now.  He'd made little secret about how important his plans were to him, and to stop now, at a moment this important?



``The mayor wants to take us back to where we were?  That's not good enough.  I'm proposing that we make this an opportunity.  The slate, in many ways, has been wiped clean.  Let's start over again.  There's national and international funding that's been put in place to help recover from Endbringer attacks and events of gross parahuman involvement.  My budget, which is detailed in handouts that will be provided in the lobby, details how we'll use our tax dollars and that recovery funding to rejuvenate the city.  The ferry, which has become a local in-joke, will be started up once more.  Low-cost, high-yield housing plans for the north end, demolition and reconstruction on a large scale for Downtown and other damaged areas, and marketing to the rest of the United States to promote and sell Brockton Bay as a symbol of perseverance and human spirit, drawing in new residents and tourism.''



``Councillor Padillo,'' the moderator spoke.  ``Any response?''



``Keith Grove is not addressing the question.  He paints a pretty picture, but he doesn't mention the presence of the local supervillains or the pressures they put on us\ldots''



I fidgeted.  Could I attack?  \emph{Should }I attack?  If I left now, maybe stepped into the side hallway, I could maybe avoid the soldiers, get to a vantage point where I could mount a counterattack against Coil.



Except I didn't know what he was planning, and my dad was here.  I could take my dad, but then I risked having to explain what was happening, and it would mean leaving Kurt, Alexander and Lacey behind.  It meant leaving all these other civilians behind.



It wasn't practical to bring anyone else along, but I couldn't bring myself to run from my dad, here.  I couldn't say why, how or any of that, but I felt as though leaving my dad behind \emph{here} would mean I could never come back.  That it would break our relationship, whether it was me getting outed as a supervillain, a break in whatever tenuous bond of trust we had or because one of us would die.



I tended to be more rational than emotional.  If I was being totally honest with myself, though, my rationalizations were pretty heavily influenced by my feelings.  I could come up with a rational justification for pretty much any course of action.  It had led me this far.  Which wasn't necessarily a good thing.



Councilor Padillo was still talking, even as my mind raced.  ``\ldotsPoints to a mismanagement of resources.  The Mayor would like us to believe that he was involved in genuine efforts to save this city.  I can't believe he would want to be associated with the PRT's operations as of late.  Loss after loss on the part of our heroes.  The losses aren't the fault of the heroes, it's even \emph{understandable, }given the sheer power wielded by the likes of the Endbringer, of the Slaughterhouse Nine and the various other threats within the city\ldots''



Coil was moving, now, his people getting in rank and file around him, his pet parahumans standing by.



I had to make my call.  Stand up to him and jeopardize everything I'd been working towards?  Here, now, with Coil drawing on his power, with three parahumans and no less than twenty elite soldiers who I knew were entirely capable of hitting what they were aiming at, backing him up?  Even if I stayed hidden in the crowd, I couldn't say for sure that he wouldn't spot me or my dad and order one of his people to move.



The alternative was that I could do as I'd been ordered, avoiding any costumed activity; trust Coil and his power to handle the situation.  I hated him, on a level, but I knew he was smart.  And I knew he knew I was here; I'd asked Lisa and she'd asked him if it was okay.  He had to have a plan for dealing with me if I took any action.



``\ldotsOpen fighting in the streets.  No, the blame lies with the PRT and the mayor's administration, which he admits was heavily involved in the decisions made.  \emph{Highly questionable} decisions:  Holding back when they could have intervened.  Forcing confrontations when our heroes were gravely outmatched.''



I saw Piggot shifting uncomfortably in her seat at that.  Had this been arranged?  A staged scene?



Coil started striding for the closed double doors that led to the back of the auditorium, flanked by Circus and the other parahuman, rank after rank of his soldiers following.



I gripped my dad's hand, held it tight, and stayed where I was.



The doors banged open.  Coil, Circus and\ldots \"{U}ber was with him, in a heavy metal suit, Leet stood off to one side, holding what looked like a ray gun.  People screamed, and it set off a chain reaction of responses throughout the auditorium.  People started running for the other exits, only to have their paths barred as more soldiers emerged.



My dad and I stayed in our seats, and I crouched low in front of my seat, pulling my dad down so he would be under cover.



``What the hell?'' the Mayor growled into his microphone.  ``\emph{Coil}?''



``Mister Mayor,'' Coil spoke.



``This is insanity,'' Grove spoke.



``Genius sometimes looks that way to those who don't see the whole picture.''  Coil had advanced far enough down the aisle that I could see him clearly.  He turned to take in the crowd, and for one heart-stopping moment I thought he'd stop when his eyes fell on me.  His head kept moving, and he walked further down the aisle, closer to the stage.



Grove said, ``The local heroes-''



``Are occupied.  Fires started at select locations, areas where the damage won't be immediate, but where they cannot be allowed to spread.  One such fire is at your headquarters.  My apologies.  I wanted to target high-priority areas.  The other fires will occupy the members of the Undersiders and Travelers and slow them down as they recover from the loss of their individual headquarters.''



I tensed at that.  How much of it was a bluff?



``You bastard,'' the Mayor growled.  ``First my niece, now this?''



Niece?



Of course.  I'd heard Dinah was niece to one of the mayoral candidates.  I hadn't realized she was the niece to the \emph{mayor}.



``She's safe and sound,'' Coil said.  ``As are any people here without a title.  If you're the mayor, or a \emph{candidate} for mayor, if you call yourself chief of police, lieutenant, director or major, I'm afraid I \emph{can't} promise your safety.''



``What are you going to do?''



``Let me demonstrate.  Circus?''



Circus was walking through the assembled crowd as though she were on solid ground, but each footstep was onto the back of one of the auditorium seats.  She extended her arms out to either side, fingers splayed, then closed her hands into fists.  Knives stuck out from the spaces between each finger.



Mr. Grove and Mrs. Padillo ran first, and Mayor Christner was only steps behind.  It didn't matter.  Circus flung her arms forward and each of the eight knives hit the mark.



People stood from their seats and for long moments I couldn't see what happened on the stage after that.  I only felt the bodies hit the floor with the bugs.  I didn't dare move the bugs to try to see exactly where the knives had landed.



Coil's soldiers were holding the reporters and cameramen at gunpoint.  I raised myself up high enough to see him turning around to face the largest group of cameras.  ``The other villains want to seize the city from below.  To start at the streets, out of sight, to remove any who would threaten their rule, and claim the various districts one by one.  They ignore the fact that there are others in power who aren't superhuman.  Ordinary mortals with the power to make decisions that affect its citizens.



``I would take the more direct route.  Brockton Bay is mine.  I will make the decisions, claim and distribute the taxes and decide who sits in seats of power.  Anyone who would disagree will face the same fate as the mayor, Mr. Grove and Mrs. Padillo.''



I rose up enough to get a glimpse of the stage.  The mayor was lying on his back, chest rising and falling with too much force, as if he was sucking in lungfuls of air and then forcing them out with just as much strength.  He had a knife sticking out of the middle of his torso, another in his shoulder, and yet another in his leg.  My father pulled me down before I could see the others.



The mayor wasn't dead, but he looked like the man might be dying.  Was I condoning this by staying silent?  I'd told myself I would let Coil's plan play out until he did something unconscionable and this threatened to cross the line.  It was only the fact that the mayor was still alive and the fact that I couldn't think of what I might do to intervene that kept me on the sidelines, hiding from the soldiers and the assault rifles they were wielding.



``You cannot expect this to succeed,'' the voice blared over the speakers.



``Director Piggot,'' Coil spoke.  ``I must admire your courage, putting yourself in the line of fire so soon after your last escapade.  Kidnapped by the Undersiders, weren't you?''



Through my bugs, I could sense how Piggot was leaning heavily on a desk just in front of the stage, using the debate moderator's microphone.  ``This plan of yours was doomed from the outset.  Just for what you've done, threatening these people and ordering the execution of those three on the stage, they'll send the entire Protectorate after you.  America will demand it.  Or are you so mad you think we'll \emph{let} you crown yourself king?''



``Mad?  No.  A monster?  Maybe.  Better to say I'm a freak of nature.  My power is to control my own destiny, to reshape and cultivate it.  What you see here is only the tip of the iceberg.''



``There's a greater plan, then.''



``Quite.  A shame you won't discover it.  Circus?''



Piggot backed away from the table and ducked low.  It didn't help.  Circus lobbed a throwing knife into the air, so that it arced.  She didn't have eyes on the director, but the knife nonetheless went high, catching the light as it reached the peak of its flight near the high ceiling of the auditorium.   It plunged down to strike its target and screams sounded from the front of the auditorium.



``Someone contacted the heroes,'' Leet spoke.  ``My U.I. says they're on the way.''



``Good,'' Coil responded.  ``Circus, come.  Squad captains, maintain order here.  We'll be back the moment this is done.''



``The bitch is too fat.  Thinking I didn't hit anything vital,'' Circus said.



``See it through,'' Coil ordered, turning to leave with \"{U}ber and Leet accompanying him.  Circus turned to follow, flicking her wrist hard over her shoulder.  Three knives traveled through the air, their paths eerily in sync as they nearly touched the ceiling, converging together as they dropped towards Piggot.



I barely had time to think about it, rising to my feet and calling on my bugs.  I knew it was too few, too late, but standing by while someone got murdered?  Four or five cockroaches, some houseflies, it wasn't enough.  I'd held the bugs back, keeping them in out of the way areas, and now I didn't have enough to block the knives or divert them from their path.



There was a flash of light around Piggot, and for just an instant, I thought maybe she had powers.  Maybe she'd had a trigger event, or she always had them but kept them in reserve?



But it wasn't her.  Weld caught the knives, letting them sink into his palm, down to the hilts.



It was the Wards.  Weld and Vista were at the foot of the room.  Vista was raising her hands, folding the walls into barriers to block those of Coil's soldiers who weren't holding the reporters hostage.  Kid Win was at one corner of the room, firing what looked like concussion blasts into soldier and civilian alike, a gun in each hand, and the hovering turrets at his shoulder adding still more firepower to the fray.  He'd taken the fight out of them with the first barrage, and the follow-up fire was apparently to take down the soldiers who managed to climb to their feet or raise a weapon.  The concussion-cannons were obvious nonlethal weapons from the casual way he was firing into the massed people, intended to stun and disable rather than harm.



Chariot had a gun that was firing off charges of electricity, similar to the one I'd borrowed from Kid Win, and was flying over the assembled soldiers, unloading shots on them.  His costume was different from the last time I'd seen him, with single-wheeled roller blades at his toes and a flight system that didn't seem to be attached to him.  A disc the size of a car tire floated behind his head and shoulders, almost luminescent with energy, and the wings of his flight suit, tipped with jets of gold light, floated out to either side of it.



Clockblocker formed the final part of the strike party.  He wasn't fighting- not directly.  He stood by a white cloth that had been frozen in time, covering the soldiers.



They were turning the situation around.  The suddenness with which they'd appeared, their positioning, they had planned this, assessing the situation, deciding where they needed to be to make a decisive strike and protect the crowd, and they must have teleported in.  I knew they had the technology to teleport \emph{objects}.  I hadn't guessed they had it for people, too.



``This way!''  Weld bellowed.  ``Evacuate through the area at the back of the stage!  Stick to the sides!  And I need medical help for the wounded!''



Their group was a little battered, beaten and bruised, and they wore replacement costume parts.  Where I could see skin, I noted the welts of bug bites and stings that hadn't yet faded.  Vista had covered hers with makeup, but they were there.



I was frozen by indecision.  I felt almost \emph{hopeful}, strange as that sounded.  If the good guys got the upper hand, if they actually beat Coil, then I could rescue Dinah by simply visiting Coil's base and opening the door to her room.  Coil was being ruthless here.  At his orders, four people had been wounded to the point that they might die.  If I stepped in to help\ldots



No, my help wouldn't be welcome.  It could even be dangerous, a distraction at a crucial time.  I would also have to escape.  A resounding victory might see them locking down the area to take down witness statements or make sure no soldiers removed their uniform and slipped out with the crowd.  Nobody had seen me gathering the bugs in my futile attempt to try to help Piggot.  But if they found out Skitter was in the building and won, then it would be a question of narrowing down which teenage girl in the building fit the profile.



And if I tried to help and \emph{Coil} won, well, my dad and I would be fucked.  No sense in putting it politely.  He would be in a prime position to not only retaliate, but maybe even retaliate without losing the support of my teammates.



If anything anchored me in place, it was the way one of Dad's hands clutched my own, the other hand holding my wrist, and the way he seemed to be trying to shield me with his body.  His face was taut with fear, his body rigid.



``Wards!''  Weld shouted.  ``All clear!?''



``Clear!''  the cry came back three times, from Clockblocker, Kid Win and Chariot.  The soldiers had been taken down.



My dad tugged on my hand.  Enough people had made their way down the aisles that we had room to maneuver.  I followed his lead, letting him pull me towards the aisle.



``Regroup!  Optimal range, facing the doors!''  Weld ordered.  Vista, Clockblocker, Kid Win and Chariot hurried to the center of the room.  He stayed where he was, watching as civilians from the crowd tended to the wounded.  All but the mayor were apparently alive.  The only one I could wonder about was the mayor.  He was lying prone, receiving CPR at the hands of two people.



``Now!''  Weld shouted.



Clockblocker moved, lunging three feet to his left to tag Chariot.  Chariot froze in the air.



I stopped in my tracks, momentarily confused.  Had some of the Wards turned traitor?  No.  Kid Win and Vista seemed to be taking this in stride.  Both were working together to bind Chariot.



There were cries of protest from the crowd.  ``What are you doing?''  ``He didn't do anything!''



``He's a double agent,'' Weld spoke, his voice carrying.  ``Working for Coil.  Go.  Evacuate, get out of here.  We have this in hand.''



He radiated confidence.  Damn it, for all the times we'd fought the Wards, for every time I'd cursed the heroes for not doing what I needed them to do, I began to feel hopeful.



My dad and I were making our way down the aisle, past the soldiers that Chariot had laid low.  We were at the steps leading up to the stage when the doors slammed open.



\"{U}ber led the way, followed by Coil, Leet, Circus and a squadron of soldiers.  His metal frame took the brunt of the incoming fire, and he used his arms to shield his exposed upper body from the blasts of electricity and the concussion shots from Kid Win's guns and turrets.



Vista began shrinking the arms, but the progress seemed slower.  She had trouble using her power when there was living material in the way, but it was still working.



Being so close to the fighting, to the gunfire and flashes of electricity, people were reacting badly.  Screaming, shouting at others to move faster, pushing and shoving.  Worst of all, they were making so much noise I couldn't follow everything that was going on.  Coil was saying something, his words carrying to the heroes, but I missed it in the chaos.



I didn't want to out myself as being present, so I was limited in how many bugs I could deploy.  A small handful on Coil served to let me follow his movements.  He'd dropped to one knee behind \"{U}ber, and Leet handed him a small remote control.  He wasted no time in pressing the button.



The noise of gunfire changed.  My head wasn't the only one that turned to see what had happened.



Kid Win had stopped shooting, and a shrill whine was filling the air.  He turned to Weld, who began tearing at his armor.



Leet stepped out from behind \"{U}ber and shot Vista.  She was thrown down the length of the aisle, slamming against the base of the stage.  He took another shot at Clockblocker, who froze himself.  Kid Win drew another gun from a side holster and shot Leet.



Weld had finished dismantling Kid Win's armor, freeing what looked to be a power cell.



I could barely make out the words, but someone in the crowd did.  A woman screamed the words, ``He said it's a bomb!  Sabotage!  Run!''



In that instant, the crowd became a crush of bodies, each trying so hard to get up and through the stairwell that we barely made any progress.  \"{U}ber, Leet, Circus and Coil began running towards the lobby, \"{U}ber kicking down the door, leaving the heroes to deal with the bomb they were holding, which was squealing at a higher pitch and volume with every passing second.  It was glowing, brilliant in its golden radiance.



Kid Win pointed at Chariot.  The boy was frozen, still, but the wings and pack on his back were still active, not attached to Chariot's suit and therefore unaffected by Clockblocker's power.



Weld caught the setup out of the air, tearing away the outer casing the second it was in his hands.  Kid Win changed the wiring.  They were shouting something to one another, but I couldn't make out the words.  Weld pointed up.



The bomb or sabotaged power supply disappeared, teleporting away in the same grid of lines that I'd seen Kid Win use to summon his massive cannon.  It dawned on me what they'd done.  Teleporting the bomb straight up into the sky, where there was nobody and nothing to be affected.



Or that had been their plan.  It didn't work out that way.  I saw a flicker of light from the lobby, the glow of the device, and Coil wheeling around to face us, his screaming lost in the midst of the shrill whine and the shouts of the others.



My eye to brain response was too slow to process everything that happened next.  I saw it in snapshots: the swelling energy of the sabotaged power supply, Coil's body coming apart in pieces, the chairs of the auditorium and fragments of floorboards being thrown into the air as the explosion seemed to move in slow motion.



Then it hit us, and I saw only white, felt only pain.





