





\emph{Heavy}.  The weight of the body on top of me was making it hard to breathe.  Some backup process kicked into gear as my body tried and failed to take in air.  I was thrust out of unconsciousness, or out of the semiconscious daze I'd been in.  I managed to struggle to get my upper body free, fighting past the aches that made every joint and every bone hurt to heave the body off me.



It hadn't felt like sleep, or the darkness of unconsciousness, but I hadn't been thinking either.  I felt a moment's disorientation and wondered if I'd suffered another concussion.  My thoughts felt too lucid.



\emph{The body.}  My dad?  I opened my eyes to look, saw only cloudy white.  Dust?  It was similar to when I woke up with bleary eyes, but no matter how many times I blinked, I could only see a white haze with vague patches of light and dark.  Blinking made my face burn where the skin of my eyelids and around my eyes moved.  More irritating was the sensation that I had something in my eyes, except no amount of blinking was helping.  They'd been damaged?



Stupid to look straight at the explosion.  I'd thought I had another half-second to grasp what was going on before I had to turn my head and shut my eyes.  Apparently that wasn't good enough.



My dad.  Right.  I reached over and fumbled to find his throat.  He had a pulse.  I put one hand in front of his mouth and found him breathing.



I was whole, he was alive.  Anything else would be hard to verify.



I was forced to use my bugs to see.  What their eyes processed might not translate well in my brain, but it was about as good as what I had.  Didn't want to move the bugs or gather a swarm.  It would be too easy to track me down, to find Skitter lying among the wounded.



No, I only looked, keeping the bugs where they were, and feeling things out where necessary with only a handful of flies.  I could feel a breeze.  The front of the building had a hole in it.  The lobby had been annihilated, and much of it was open to the sky.  The black blobs that had pulled up around the building had flickering lights on top.  Sirens.  They would be the first responders.



I'd noted the structural damage.  I tried to picture the scene as I'd last glimpsed it.  What had been where?  \emph{Who }had been where?



The reporters had been at the very back of the room, the last to make their way down the aisles in the press of the crowd and the people making their way out of their seats.  Some had lingered, protecting their equipment or filming the scene.  I tenderly moved one fly over the area, feeling the shattered boards, the blood-slick expanses of floor, the charred flesh.



Several of the Wards were working to tend to the wounded.  Clockblocker had saved the Wards, apparently, but had been too late in tending to himself, and was currently lying prone, receiving some care from Weld.  Chariot was gone.



There had been hundreds of people present, and too many had still been in the building when the explosion went off.  The dad and son who'd been restrained in the lobby?  The mayor, candidates and director who'd been wounded, then left without aid when the explosion injured the people who were giving them first aid, sent the people flying?



I couldn't even grasp the entirety of the scene, not without bringing my swarm to bear.  I couldn't do \emph{that} without possibly revealing my presence when I was in a vulnerable position.



I felt around to find Kurt and Lacey.



``Hey baby,'' Lacey said.  ``You woke up.''



``You hurt?''



``Just a little bit.  Might have slipped a disc.  Probably nothing to worry about, but I'm going to stay as still as I can with how bad this hurts.  I've been watching your dad, trying to tell if he's breathing or if I'm imagining it.  You didn't freak out, so I take it that our Danny's okay?''



``He's okay.  I think.''



``Good.  Kurt's unconscious but he's alright.  You see Alexander anywhere?''



I blinked a few times.  Did she not realize I couldn't see?  ``No.''



``Okay, hon.  You should stay as still as possible.''



I shook my head.  ``No.  Going to see if anyone needs help.''



She gripped my hand, started to say something, then winced.



``What's wrong.''



``Hurts, is all.  Stay put?  Safest thing to do.''



I shook my head.  I couldn't say it, but I felt like I'd been through enough crises and suffered enough that I was aware of what the pain was telling me.  I was almost certain I wasn't in critical danger.  It was what my gut was telling me.



With only a small few bugs to guide me, I left my dad, Kurt and Lacey behind, climbing up the stairs to the damaged stage, fumbling for the other wounded.  I could only draw crude images of the situation from touch, from the blurry images my eyes offered me and through my bugs.  A woman, unconscious like my dad.  A man, his arms hugged to his lower stomach as he writhed in perpetual agony.



The mayor.  I crawled over to him, pressing my fingers to his throat.  He had a pulse, but it was thready.  I drew bugs from where they hid in the midst of my hair, commanded them down my arms and tried to bend over so my hair masked what I was doing.  Once they were on him, I sent them over the length of his body, noting where there was blood.  No use fumbling around with my hands.  I didn't want to bump one of the throwing knives and gave it the push necessary to drive it into one of his arteries.  One of the knives that impaled his hip had moved, probably when the explosion happened, and the offending weapon wasn't serving to cork the blood flow.



I pulled my sweatshirt from around my waist, leaving my knife where it was on my belt, folding one sleeve and pressing it around the base of where the knife had penetrated.  It wasn't enough, didn't feel like I was doing anything, but I wasn't sure what else I could do.  I wasn't strong enough to do chest compressions.



``Help!''  I shouted.  ``I need help here!''



Nobody leaped to the rescue.  Anyone else that was still in the building was too busy with their own injuries, were still unconscious or were making their way outside.



Damn them.



Damn \emph{Coil}.  I would make him answer for this.



Yes, I had seen `Coil' die.  I had little doubt others had as well, even news cameras would have had eyes on the scene.  \emph{Especially }news cameras.  Coil had staged this, taken advantage of the reporters' cameras, the fact that there were no working communications, and all the important figures would be attending.  He was too savvy, too invested in his plan to not have taken all the variables into account.  Just the fact that I knew about his power turned this whole scenario on its head.  He wouldn't have charged in like this without a backup, without a version of himself staying safe and secure in his underground base, just in case things went awry.



No.  I might have seen the man die, but the more I thought about it, the less I could believe that man was Coil.



The emergency response team had stopped outside, at the perimeter of the building.  I listened through the bugs in the area, but I couldn't follow any of the conversation.  Even tracking who was speaking was nearly impossible.



Whatever they had been discussing, they ventured inside.  Some, who I gathered might be police officers, were moving to the most affected areas, the places where the reporters had been, the lobby.  The paramedics proceeded down the aisles, too slowly for my liking, checking on the wounded.



``Help!'' I called out, but my voice was nearly drowned out by the other wounded.  It was one or two minutes before a paramedic saw the mayor and hurried to my side.  I could tell where he was because of the bug I'd planted on him, but I couldn't say as much.



``I've got this,'' she said.  The paramedic was a woman.



I gratefully backed away.  Even the strain of pushing the makeshift bandage down had been making every ache and pain across my body stand out in sharp relief.



``Your name?'' she asked me.



``Taylor.''



A short distance away, my dad groaned a response, as if he'd heard my voice.  I noticed more because of the mosquito I'd placed over his carotid artery than my ears.  I didn't let on that I'd noticed anything.



``You shouldn't be moving, Taylor.''



``I'm sore, but I don't think I'm \emph{hurt}.  I wanted to help.''



``What kind of pain?''



``Bruises, aches.  My dad took the brunt of it,'' I pointed in his general direction.  ``My face hurts, and, um, I can't see.''



``Don't worry.  Soon as we take care of the critically injured, we'll look after you.''



``I'm alive,'' I said.  ``I mean, I'm okay.  I'd rather you guys checked my dad and his friends, make sure they aren't hurt, help the other candidates, and the Director.  They were stabbed before the explosion.  All of them like this.  Um.  They were getting help when the bomb blew.  I think whoever was helping them got knocked away by the explosion.''



I was rambling.  How fine \emph{was} I?



The paramedic shouted, ``Boroughs!  Sturdevant!  Manry!  Girl here says there're MSW victims on the stage here!''



I could hear running footsteps, one of my bugs brushed against one of them as they ran past.



There wasn't much more I could do.  I'd gladly out myself if it meant I could use my power to help people, maybe identify the most wounded, but I was worried it would do more harm than good, both in the short-term and in the long.  I was left to sit there, blind, while the paramedic checked my dad over and then got someone else's help to lift him to the ground.



As the paramedics checked whether people were alive, others were rousing.  I could hear the cries of pain, the shouts and screams.



Coil would answer for this.  For the people he'd hurt for his own selfish ends.  For knowingly putting me in the line of fire.  For the lives he'd spent like currency.



``Taylor, was it?'' the paramedic asked me.



``Yeah.''



``You're very quiet.  You're breathing hard-''



``Angry.  And a little sore.  But I'm okay.  Really.  There're others who need help.''



``Others are \emph{getting} help.  We've got a lot of people here, and very few with serious injuries.  You have a burn on your face, we're going to want to look after that.''



``The reporters, at the back of the auditorium-''



``I thought you couldn't see.''



``I remember seeing them there, just before it went off.''



``Very few people were badly hurt.  Less than you might think.  Just stay calm.''



If I hadn't used my bugs to see the evidence for myself, would I have been able to tell she was lying?



She wanted me to stay calm.  It was odd, but I felt \emph{very} calm, and I didn't feel like I was in shock.  I was pissed, I was worried about my dad, worried that I was missing something critical with Coil's overarching plan, but I wasn't panicking, I wasn't stressing about the burn, or my eyes, or any of that.



I'd handled worse, in terms of injuries.  I wouldn't freak over that much.  I'd\emph{ love} to be able to see what was going on, to not have to worry about permanent blindness, but I wouldn't worry about it until I could confirm how bad it was, confirm that it \emph{was} permanent.



Sort of like how I was looking at the potential end of the world.  I wouldn't worry about it until we'd exhausted every resource available and verified that in this era where countless people had the ability to break the fundamental rules of reality, \emph{someone} couldn't stop it from happening.



``I \emph{am} calm,'' I said, after confirming it for myself.  I tried to take a deep breath to demonstrate, but winced at the pain from the bruising.  I might have been pushed into the railing by the force of the explosion.  ``But I don't want you to worry about \emph{me}.  My dad-''



``The bald guy by the stairs?''



``Yeah.''



``My partner's looking after him.  Let's make sure \emph{you're} okay.  If there's spinal damage or internal damage and we're ignoring it and letting you move around like you have been, things could get much worse than they are now.''



I shut my eyes, noting how the blurry white haze gave way to darkness.  I could remember when Leviathan had hit me, how Panacea had noted internal damage that I'd been entirely unaware of.  I sighed, opened my eyes to stare at the hazy figure.  ``Okay.''



``We're going to be putting you onto a stretcher, but we won't be carrying you out for a minute.  We can't leave you alone, but I'll need to help my partner carry your dad out.  What we're going to do is put you next to someone, so someone can watch two or three of you at once.''



``Okay.''



I was lifted into place, then carried a short distance before being set down with great care.  The paramedic there was talking with one of the other patients, leaving me free to think.



\emph{Why?}



That was what got me.  This whole thing bordered on senselessness.  Hurting these people, putting me in the line of fire.  Why attack the event?  It would draw attention from heroes across the nation and it would make holding the city that much harder.  Had he abandoned the plan?  Or were there nuances I wasn't aware of?



What was deliberate, in how this had unfolded?  He'd wanted to take out the mayor.  But the candidates?  Hadn't they been his?



I was looking at it the wrong way.  Circus.  She had been part of the plan from the beginning, and he'd hired her for an explicit reason.  Her powers included her personal pocket dimension for storing items.  I couldn't think of how that might be used.  She had minor pyrokinesis, but that didn't apply here, either.  She also had an enhanced sense of balance and enhanced coordination.



The balance wasn't a major thing here.  But the coordination?  The way she'd been able to casually target Piggot as she tossed the throwing knives over one shoulder?  If I had to guess, Circus' knives had only killed the people Coil wanted dead.  The others would have been hit in nonvital areas.  Her enhanced hand-eye coordination would have given her the accuracy needed to ensure the knives hit where she wanted them to hit.



\"{U}ber, then?  Leet?  What was the rationale for them?  When we'd left the fundraiser and Coil had revealed himself as our employer, it had been Trainwreck in Coil's company, but Trainwreck had joined the Merchants, possibly at Coil's behest, and the Merchants had been eradicated.  He was dead.



That led me to wonder if Coil had brought in \"{U}ber as a stand-in for Trainwreck, wearing another heavy metal suit.



Was there a reason for why Coil wanted it?



Circus, \"{U}ber, Leet, Chariot, the candidates\ldots moving parts in a greater set of machinations that I wasn't aware of.  The reporters, me, my dad, and any number of people in the area, we were the bystanders, the casualties.



And I couldn't get \emph{why}.  Was it to attack or assassinate the mayor and Director?  To mark his candidates as survivors of a supervillain attack and give them more standing in the eyes of the public?  It didn't make sense.  Why go to the effort of positioning the Undersiders and the Travelers in the city if that was his goal?  Any advantage he might glean from us holding territory would be counterbalanced by the chaos and the national attention that he drew from this kind of terrorism.  It wouldn't be directed at \emph{him}, because his body double had been killed in the attack, but it couldn't \emph{help, }either.



If I thought about it, I could almost believe the bombing had been intentional.  I couldn't say how he'd arranged it, but the fact that he'd thought to have a body double and the man had died and that `Coil' was effectively off everyone's radar seemed too coincidental.



It was something I needed to ruminate on.  Minutes passed, and I was left with only my bugs to occupy me, and the periodic attention of the paramedic who'd been assigned to watch me, making sure I was still alive and lucid.  I directed bugs into the rubble, beneath the chairs that had been unrooted from the auditorium floor, under and onto bodies.  Slowly, I gained a greater picture of the scene, a topographical map of what Coil had done.  I couldn't count the bodies, not with the way the reporters had been pulverized, limbs and bones torn free and left lying beneath chairs or at the sides of the aisles



``We're moving you now,'' a man said.



``Me?''



``Yeah.  Just stay put, don't move.''



I was lifted into the air, carried past the ruined wall at the rear of the auditorium.  I could smell the scent of death, the mingled smells of blood and shit, of human bodies that had been torn open, singed, the vitreous fluids and all the messy ugliness from inside our bodies exposed to the air.  It seemed incongruous with the cool breeze and the gentle warmth of the sun on my face.  I had to turn my head so the sun wasn't shining on the burn.



Shouldn't a catastrophe like this be met with rain?  An overcast sky?  It didn't seem right that things were so quiet, so calm, the day so tranquil when so many people had died, lost loved ones or suffered serious injury.  I bit my lip, focusing on my bugs, sweeping them through the area as the ambulance made its way to the hospital and the paramedic in the back carefully checked my vitals, asking me questions about the degree of pain, stiffness here or there and checking for hard tissue where there might be internal injuries.



It was odd, going to the same hospital where I'd been taken after fighting Leviathan.  I maintained a few bugs to feel things out – a stray housefly or mosquito would likely go unnoticed if it kept out of the way.  There were no capes, no blue tags or red tags on the curtain rods, nor PRT uniforms keeping order and informing the staff of who they were treating.



They took me to a curtained off area, very similar to the one I'd been in before.  Except here I was Taylor, not Skitter.  I wasn't handcuffed, treated roughly or outed for my most damaging secrets.  They investigated me thoroughly, shone a light in my eyes and asked me far too many questions.  A cream was spread across the mild burn on a quarter of my face, and the nurse picked grit out from beneath my skin.  The process hurt, but it was a two at most on a scale of one to ten.  I'd dealt with tens before.



The fact that I couldn't see was starting to wear on me.  My left eye was worse than my right, but neither let me see details, only smudges.  Only light and dark.  I was so used to having an unnaturally broad sense of what was going on, but I'd just had one of my most essential senses stripped away from me.



As the medical professionals left, a young woman slipped into the curtained enclosure.



``Hey,'' she said.  ``You're alive?''



``Lisa?''



``Yeah.''



``Honeybee-T.''



``Praying-mantis-R.  You're blind.  \emph{Damn}, that sucks,'' she said.



``Yeah,'' I sighed.  ``My dad?''



``He's okay.  Looked in on him.  He woke up and was asking after you.  He doesn't like me much, anymore.''



``You took me away from him.  He'll blame you for that because it's easier than blaming me, I guess.''



``I guess.''  I planted a mosquito between her shoulder blades, and I could track her as she stepped closer, crouching with her arms resting on the rail of the hospital bed.  When she spoke, she was quiet enough that only I could hear her.  ``We can get you a healer or something.  Kidnap someone like Othala, have Regent or Grue use her powers.''



``Othala isn't around.  Left the city.''



``We'll hire someone with healing powers, then.''



``They won't want to come here, because of the very thing you were talking about with Othala.  Word's probably out about us owning the city, especially after we kicked out groups like the Chosen, and Faultline's crew.  They'll tell people just how dangerous we are, the kind of tactics we can employ, like using Regent or Grue.''



``We have options.''



``I know.  I'm not worried about \emph{me}.  What gets me is what happened.  So many were hurt or killed.''



``Lots hurt, not so many killed, from what I've seen and heard on the subject.  But that's not important right now.  What are your priorities?''



I blinked.  ``My dad-''



``Is fine.''



``My territory, the fires?''



``Strategically placed, nowhere near our real lairs.  Nobody hurt, but I think he molotov'd one of your barracks, setting the fire high so people had a chance to get out.''



``The others, Grue-''



``They weren't anywhere nearby.  We're going to meet up with them soon.''



``Dinah.''



``\emph{Now} you're on track.  We've talked about plans.  And Coil-''



``He's alive, right?'' I asked.



``Mm hmm,'' Lisa affirmed.  ``And better for us, he's probably \emph{happy}.  Everything's coming together for him, just the way he wanted it to.  Which means that right now, \emph{today}, is going to be our best bet for talking to him, getting at him when he's in a mood to release the tyke.  Come on, out of bed.''



My head was spinning, but it wasn't a concussion at work.  After everything I'd done, everything I'd put in, we were this close?  I accepted Lisa's help in getting out of the hospital bed, and she hooked her arm beneath mine to lead me away.



``So we just ask, and hope he's feeling good enough to say yes?''  \emph{Which means biting my tongue when it comes to the accusations}, \emph{calling him on what he did at the debate.}



Lisa spoke at a more normal volume, ``He doesn't strike me as the kind of person who'll be influenced much by his emotions.  He probably decided a while ago whether he'll give up the girl or not.  But I say we should take anything we can get, and that includes approaching him on a good day.  Choose your words carefully, by the way.  There's bystanders.''



I nodded, but I didn't follow as she tugged on my arm.  ``Can we check on my dad before we go?''



``They were moving him when I poked my head in.  I peeked at his chart, and it looks like they had queued him up for an MRI, what with his recent internal injuries from Shatterbird's attack.''



I winced.



She went on, ``I told him I might take you to my dad's clinic, where the load won't be as high, if you were okay to be moved.  If I \emph{did} take you,\emph{ }it'd mean you were okay.  He didn't like that, but he agreed.  That doesn't mean we can't stay if you want to stay.  Like I said, it won't make a huge difference if we get in touch with our boss now or two hours from now.''



``But it'll make a difference?  A bit of one?''



``I think so.''



I thought back to my earlier feeling, that leaving my dad just the one more time might mean some kind of terminal break.



Stacking that up against everything I'd done with the end-goal of getting Dinah out of captivity, though\ldots not even \emph{Dinah}, exactly.  I barely knew her.  No, this was more selfish, I had to admit.  I was thinking of my own sense of guilt, about my own responsibility, and the crimes I'd committed in getting this far.  The terror, pain and distress I'd caused in the course of being Skitter.



Fifteen and a half years spent growing up with my dad versus two months as Skitter.  My dad was \emph{there}, though.  He'd always been there, and the only thing I had to suggest that he wouldn't was a vague feeling.



Just like there was only the vaguest possibility that our going to see Coil \emph{now} would make the difference in him setting Dinah free.



``My dad's going to be okay?'' I asked.



``He was fine.  No sign of any deeper problems or pain.''



``Then let's go.''



We made our way out of the hospital.  I could hear the cries of pain.



``Are we to blame for this?''



``No.  Don't set yourself on this path.  We didn't know, we \emph{couldn't} know, and we weren't complicit in any way.''



``I was there.  I could have stepped up and done something, but I didn't.''



``Done what?  Fought back?  Helped the wards?''



``\emph{Yes.}''



``No.  Best case scenario, you might have tripped him up.  But it wouldn't have been worth it.  Watch your step.  Stairs.''



I had no problem identifying the spots I was supposed to step down.  There were spiders on the underside of the stairwell, and I sent a few flies forward to alight on the underside of each stair to check the footing.



``It's funny,'' Lisa murmured, lowering her voice, ``I've been meaning to suggest a training program.  That you should spend a while blindfolded, see if we can't force you to rely on your power to see, get your brain to the point that you can actually process that info.  Guess you beat me to the punch.''



``It's not that funny,'' I said.  I didn't like thinking about what might happen if I was still blind when the \emph{next} disaster came along.



``Stepping outside,'' she said.  I felt the warm air sweep past me as the door opened.  ``Car's just over here.  Nice thing about the city being in this state, it's easy to find parking spots.''



She sounded so jovial, cheery.  I wasn't nearly so optimistic.



She led us to the car, and opened the door for me.  ``We'll stop by your place so you can grab your costume and meet up with the others.  Then we'll find Coil.''



``Find him?  He's not at his base?''  I raised my voice to be heard as she walked around to the other side of the car and opened the door to get into the driver's seat.



``He's not at his base.  As of now, Coil's dead and gone.  He's sticking to his civilian identity.  Which is going to make meeting him and talking to him sort of difficult.''



I paused.  I'd been thinking over the scenario, calculating Coil's overarching goal.  ``Is he Keith Grove?''



``No,'' Lisa said.  ``One sec.''



The car started up, and there was a shuffling sound as she dug through a container.



A recording played over the car's sound system.  Lisa shifted the car into gear and reversed out of her spot.  I listened.



``A town meeting with hundreds of Brockton Bay residents was interrupted by a terrorist attack by a local villain just earlier today, an alleged assassination turned to even greater tragedy as a superhero-made piece of technology exploded unexpectedly.



``\emph{This tragedy joins countless others that have recently befallen Brockton Bay, a city that was recently the subject of national discussion, where the United States Senate debated condemning the city, evacuating the remaining citizens and abandoning it as a lost cause.  A local crime lord headed a small group of supervillains in an attempt to assassinate Mayor Christner, Mayoral Candidate Keith Grove and Mayoral Candidate Carlene Padillo.  When local heroes intervened, however, a device owned by local Wards member `Kid Win' malfunctioned, ultimately exploding in the lobby of the building.  While the number of casualties is yet unconfirmed, we can confirm that WCVN's own on-site reporter and camera crew perished in the blast.  More information will be forthcoming as we have it.}



``\emph{First reports from the site report allegations of sabotage on the part of a known double agent within the group of junior heroes.  No members of the Brockton Bay PRT, Protectorate or Wards teams were available for comment, but sources inside the organization report that Director Emily Piggot, manager of the city's PRT and government sponsored hero teams, is being put on leave pending a full investigation.}



``\emph{Filling in for the interim is Commander Thomas Calvert.  When asked about this new placement, the PRT reported that Commander Calvert served as a PRT field agent before an honorable discharge.  For the past several years he has offered his expertise to the PRT as a paid consultant in parahuman affairs for New York, Brockton Bay and Boston, later serving as a field commander for the PRT strike squads.  The PRT expresses full confidence in Commander Calvert's ability to handle the daunting task of Brockton Bay's parahuman-}''



The sound cut out.  Lisa had stopped the recording.



``Thomas Calvert,'' I said.





