





I pushed open the rusted metal door that marked the first real barrier to entry for Coil's underground base.  It was unassuming, if secure, easy to ignore for anyone who happened to find their way underground.  It swung open without resistance; unlocked.



\emph{Every} door was unlocked as I made my way through the series of checkpoints and gates.  There were no guards, and the cameras in the final room before I entered the base proper didn't move to track my movements.



I pushed on the final door and let it swing open.  The base was empty.  Except empty wasn't exactly the right word.  It had been cleared out.



The on-duty squads of soldiers were gone, as were the trucks, weapons, supplies and furniture.  The entire ground floor was desolate, with clean patches in the dust where furniture and crates had been.



In groups big enough for me to get full coverage of the area, my swarms took turns roving over my surroundings.  They couldn't pass through closed doors, but they gave me a sense of my surroundings that my eyes couldn't.  The results were almost the inverse of what I might expect from my eyesight.  There was no grasp of color, beyond what I could guess from the various clues I got from my other senses, but I had a keen sense of textures.  Where my eyes would have been capable of focusing on \emph{one} thing at a time, my swarm-sense gave me the ability to pull together complete mental pictures from a thousand different points of focus.  I could ignore line of sight, sensing \emph{around} objects, and even though my bugs' senses translated poorly, the sum total of their awareness gave me a sense of the little things, in addition to the big picture.  I could sense where the air currents were traveling and the force with which they moved, the thickness of the dust in one area versus another, and where temperatures where higher, if even by a fraction.



None of this was \emph{new}, exactly.  I'd always been aware of it to some small degree, but my core senses had always been there as regular, reliable fallback.  I'd never researched the subject, but reports seemed conflicting when it came to the topic of blindness making other senses sharper.  With only half of a day's experience, I was beginning to think that maybe it didn't \emph{improve} my other senses, but seemed to free up the semi-conscious, semi-unconscious intake that my eyes typically used as my dominant sense.  The brainpower that was usually allocated to idle glances, comparing and contrasting, or just taking in ambient sights while my thoughts were preoccupied with other things?  It was freed up to be used for listening and my swarm-sense.



The Travelers were here, I noted.  I wasn't startled to note their presence, but I was somewhat surprised.  They'd gathered in one room above the vault that Noelle was presumably being kept in.  They'd noticed the bugs and were venturing outside onto the walkway.  I met them halfway between their apartment and the entrance.



They were in civilian wear.  Trickster and Ballistic were in regular shirts, jeans and shoes, but Sundancer was wearing what I took to be pyjamas, her hair tied back in a bun.  Genesis was in her chair, a blanket on her lap, with Oliver standing just behind her.



``Skitter,'' Trickster said, ``You're here alone?''



``My teammates are upstairs.  We wanted to have words with Coil, but he wasn't free to talk until sundown, so we've been killing time and waiting around.  There's still a bit of time, I sensed some movement down here, I needed to stretch my legs to keep my injuries from earlier today from stiffening up, so I decided to take a bit of a walk.''



``And they're staying put?''  Ballistic asked.



``I can signal them in a heartbeat if I have to,'' I responded.



``Just saying, but you know Coil's dead, right?'' Trickster asked.



``I saw it happen,'' I answered him.  I chose my words carefully, ``So I have a \emph{very} good idea of how dead the man is.''



``Fair enough.''



``And you guys?'' I asked.  ``You're keeping eyes on your teammate?  Noelle?''



``Noelle's fine,'' Trickster said, ``You don't need to concern yourself over her.''



There was just a touch of hostility here.  I turned my head to face the two girls, using my bugs to figure out the orientation so I could appear to be looking at Sundancer and Genesis.  The two of them were, I figured, the closest thing to allies that I had among the Travelers.  That wasn't to say I was on \emph{good} terms with them; Sundancer was especially wary of me and had been since I'd carved out Lung's eyes, and Genesis had been a little weird in how she related to me when I'd delivered Trickster to her at the mayor's house.  Part of that might have been a reflection or a response to my own paranoia, where I'd thought they were planning to kill me.  Either way, they hadn't given me the impression of dislike or hostility to quite the same degree that I was seeing with Trickster and Ballistic right now.



This was where my current inability to see was hurting me.  I couldn't read their expressions or body language, and even though my bugs were giving me a sense of how they were standing and where their head, arm and legs were positioned, I didn't have that innate human ability to instantaneously assess and process those details.  Time and effort spent trying to figure it out was taken away from my ability to plan and follow the conversation.  It was sort of like talking to an answering machine; I was left trying to hold up my end of a conversation without the ability to assess what the person on the other end was making of it.  End result?  I was left there, silent, while none of the Travelers were volunteering anything.



``If you're done checking up on us, or visiting, whatever you want to call it,'' Trickster said, ``You could go.  Your duty's done, you've paid your respects to the other team while you're in their territory.''



\emph{That's something we're supposed to do?}



``I don't want us to be enemies,'' I said.



``We're not,'' Trickster replied, but his tone was far from friendly.  ``We're on the same side.''



``But?'' I asked.  ``It sounds like there's more to that.''



``We're not \emph{friends}, Skitter.  Let's not pretend like we are.  You've got your goals, we have ours.  You want to work together to tackle a situation like the Dragon thing?  Fine.  Great.  You want to backdoor Ballistic, going to the boss to recruit that cape he was trying to take down?  Hey, that's fine too.''



Ballistic folded his arms.



Trickster went on, ``Really.  We're doing what we have to do in order to make this thing work.  I don't love what you pulled, I'm not jumping for glee, but I get it.''



``So we're business associates, but not friends.''



``Succinctly put.''



``There has to be more common ground there.  We can't meet, share a box of donuts and talk about ways to mutually benefit our territories?''



``The fact that you have to ask that is a pretty good indication of how clueless you are about this. Let's count the ways.  One, I don't give a ratfuck about my territory or the people in it.  None of us do.''



I could feel Sundancer turning slightly away from him.  Was there disagreement there?



``\emph{Two},'' he continued, ``We don't plan to be here much longer anyways.  Either Coil fulfills his end of the bargain and we're out of this hellhole, or he doesn't and we take a hike anyways.  Take our chances elsewhere.''



I could remember how Ballistic had talked about his frustration with the group, the idea that he might stick with this gig regardless of what Trickster and the others did.  If I brought it up, would it refocus the discussion to the point that Trickster wasn't \emph{opposing }me, in an abstract sense, or would it derail it with the ensuing drama?



I kept my mouth shut, and I was sort of glad that I couldn't see, or I might have given in to my impulse to glance at Ballistic and give something away.



Maybe it wasn't worth worrying about.  I was wearing my full costume, including the additional pieces I'd accumulated over time; I wore the tattered cape, the ragged semi-dress over my leggings, and a heavy carpet of bugs clung to the black fabric and armor panels.  My goggles would hide my eyes.  Nobody would see any tell, if I could see, and I doubted they'd notice I was essentially blind.



Trickster took my silence for an excuse to go on, ``\emph{Three}, again, there's no common ground to be found, and I'm not interested in hunting for it.  There's two things I want in this world, and being part of Coil's thing was my way to get those things.  \emph{You} were useful only as far as you helped make Coil's thing work, and that's over now.  To put it bluntly, you don't have anything to offer me.''



``I get the picture,'' I told him, cutting him off before he could continue.  ``Okay.  Friendship's off the table.  Even a \emph{friendly} business relationship would be pushing it.''



He nodded once.



I sighed a little.  ``Okay.  That said, as one local warlord to another, I'd like to extend an invitation.  We're going to talk to Coil, and I'm saying you're free to come.''



``Coil's dead,'' Ballistic made the words a drawl.



That was getting old fast.  ``Do we \emph{really} have to maintain this charade?''



``Coil went to a lot of effort in putting together his grand plan.  He died in a blaze of glory and violence, \emph{just like he wanted}.  Do you really want to spoil that by going on about how he's still alive?''



``Like you said,'' I retorted, ``We're on the same side.  If you didn't know, you'd be more upset than you are now.  Why pretend he's dead when he's alive?  \emph{Especially} when it's getting in the way of the larger conversation about the man and my invitation to come hear what he has to say?''



Trickster leaned against a wall and fumbled in one pocket for a cigarette.  ``You mean outside of the possibility that you're wired and my saying the wrong thing could out him?  Whatever.  I don't have anything to say to him that I haven't already said.  Maybe you aren't getting the point.  We went out of our way to help you once, rescuing Grue, and it nearly got us carved up by Bonesaw.''



\emph{Your plan,} I thought.



He went on, ``I don't care about the Undersiders.  I don't care if you get a hundred trillion dollars and wind up kings of the planet, and I don't care if Coil kills you.  We've wrapped up our business with Coil, and that's as far as my interest goes.''



``Alright,'' I said, raising my hands, ``Point taken.  Listen, I get that maybe we haven't gotten along so fantastically, but I really do wish you guys luck with your circumstances, whatever they are.  I hope you get what you've been looking for.''



``Sure,'' Trickster said.  He turned to leave, making his way to the doorway that led to the pseudo-apartment they stayed in when they weren't in their individual headquarters.  He beckoned for his teammates to follow, and they did.



Only Genesis lagged behind, her hands on the wheels of her chair.  After Trickster had rounded the corner, she said, ``He's tense.  Too much comes down to what happens in the next forty-eight hours.''



``Believe me,'' I replied, ``I get that.''



``Then good luck with your thing,'' she said.  ``Don't take this the wrong way, but I hope I never see you again.''



\emph{How the hell am I supposed to take that?}



I didn't respond as she wheeled herself to the corridor.



\emph{Okay}, I thought, \emph{learned what I needed to}.



Whatever the terms between Coil and the Travelers were, he hadn't seen fit to invite them to the meeting place.  I'd had to think for some time before making the offer to join us for the meeting.  I knew that whatever Coil had planned, inviting the Travelers wouldn't hurt.



If Coil fully expected to cooperate, to give us the answers we needed and hand Dinah over, then it didn't matter if the Travelers were there.  If he was expecting conflict and he \emph{had} planned to invite them, then we only gained the benefit of knowing in advance that they'd be there.  Finally, if he'd expected trouble but he hadn't invited them, there was probably a reason, and that reason would be something we could exploit in a pinch.



They hadn't accepted my invitation anyways, and I hadn't sensed anything sinister when Trickster had rejected the offer.  He'd been too self-centered.



Funny, as I thought on it, how easily he seemed to slip between talking about `I' as in himself to talking about `we', the group.  It was as if he assumed everyone in the Travelers was on the same page as him, and my discussions with Sundancer and Ballistic had suggested anything but.  Even Cherish's taunts had pointed to some strife within the ranks.



The second major piece of data that I'd gleaned from my detour was that Dinah wasn't here.  There were a handful of locked doors my bugs hadn't been able to slip past, but the room Dinah had been in when we'd first visited was empty.  I wasn't a \emph{hundred} percent sure that Dinah wasn't still in Coil's underground base, but I had a hard time believing that Coil would leave her there with no armed guards.  She was too valuable to risk losing her to one of his enemies or losing his bargaining chip he had in his dealings with me.



We'd agreed that if I could prove myself as a valuable asset, he'd accept my fealty in exchange for Dinah's freedom.  I hadn't earned him any money, not directly, but that had never really been his goal.  He had money, and he could get more by exercising his power in some high-risk, high-reward ventures.  I \emph{had} gathered more followers under my wing than all of the others put together, with the possible exception of Tattletale.  I'd put life and limb at risk, partially for his benefit.  I'd proved myself as a leader, a soldier and a problem solver.  I'd put up with every challenge he'd set in my way: the false death threat he'd put on my head, convincing the mayor, dealing with Dragon and going up against the Nine.  Hell, I'd tended to my territory while my dad lay bleeding in the hospital.



I couldn't say for sure whether Coil would actually follow through with his end of the deal.  In his shoes, ignoring what the right thing to do would be, if only because it was pretty \emph{fucking obvious} he didn't put much stock in right and wrong, I wasn't sure I'd give Dinah up.  For a guy like Coil, who did things from behind the scenes, playing the long game and orchestrating events to get the best possible results, Dinah's power was invaluable.



Trickster had used a chess metaphor, back when the thing with the Nine was just beginning.  Would I be considered a bishop?  Hell, even if I thought of myself as a queen, I wasn't sure Coil would value having me on his side of the board over having Dinah.



Dinah let him rig the game.



I ventured outside and made my way to the flights of stairs for the building that was still in progress.  It had proceeded nicely in recent days, and the outside was partially complete.  The sun was setting, and my bugs could see and feel the warm light that streamed in through the openings in the outside, where tarps had come free.  The thick dust of concrete and shorn wood layered the area and formed clouds wherever the wind made its way inside.



I'd climbed the stairs to the meeting place only an hour ago, and I'd ventured all the way to the bottom to investigate Coil's base.  That made this my third trip over the twenty flights of stairs, accessing the roof.  On my third trip, my aches and pains from being tossed around by Coil's explosion were most definitely making themselves felt.



In a way, I didn't mind.  I felt restless, and moving made me feel better.  Nervous wasn't the right word.  Nervousness implied there was uncertainty, and I was pretty sure this wouldn't go the way I hoped.  Trepidation wasn't right either.  I might have settled on `a sense of encroaching doom' but that felt over the top.



Then again, this was someone's life on the line.  Maybe our lives too.  Was it possible to be over the top when the stakes were this high?



The others had arranged themselves around the roof.  Bitch was in a half-sitting, half-lying down position, leaning back against Bentley's side, Bastard sleeping on her lap.  Tattletale and Regent were having a discussion at the top of the stairwell, while Grue and Imp were at the edge of the building.  Imp sat with her legs dangling off the side of the building, while Grue showed more caution, standing a distance behind her.



``You should be careful,'' I spoke up.  ``If you're standing too close to the building's edge, you're making yourself a prime target for a sniper.''



``You said these suits were bulletproof,'' Imp said.  I noticed how she didn't move.



``I said they \emph{might} be.  But judging by the fact that mine let some non-metal shotgun pellets through, I don't think they'll stop a bullet.  Either way, I'd really rather not start experimenting tonight.''



Imp pulled herself to her feet and retreated from the edge of the building.  I could feel Grue's shoulders drop slightly as he relaxed.



Grue and Tattletale drifted my way, while Regent, Imp and Bitch each sort of moved to the periphery of our huddle.  It was Grue who asked, ``You think he's going to take shots at us?''



``I feel exposed,'' I said.  ``If he opens fire on us, are we really in a position to take cover?  Or if he bombs out the first floor of the building?  Or calls in the teams of heroes he's in charge of?  Could we really get down?''



``I'm not getting that vibe,'' Tattletale said.



``But he's figured out how to trick your power,'' I pointed out.



``Any solutions?'' Grue asked.



``Yeah.  I've been working on one, but I'm not sure it'll work.''



``Share?''



I extended one hand, and a wasp took flight, bearing a trio of spiders.  It was forced to turn and fly in circles to slow its forward movement to account for the speed at which the spiders were spooling out thread.  The ends of the thread were already wrapped around one of my fingers.



It took a minute before they reached the other formation that was doing the same thing.  I began reeling in the thread, until I'd raised a length of cord to the edge of the roof.



Bitch ventured over to see what was going on, and then spun around, ``No.''



``My first night out in costume, I got stuck on top of a building.  I'm not going to make the same mistake twice.  We called Thomas Calvert, he agreed to meet us, but \emph{just in case} he decides to level the building rather than have a conversation, I want us to have a way down.''



``A way down?'' Grue asked.



``I'm pretty sure I got the lengths right.  I \emph{hope} I got the lengths right, because I used up a lot of silk here.  Eight cords, we each hold one, or tie one around our waists, and then jump off the side of the building.  Swing out over the intersection.''



``\emph{Awesome},'' Imp said.



``\emph{Pretty} sure?'' Grue asked.



``Pretty sure,'' I admitted.  ``I've tried to stagger it, so the silk stretches out over horizontal lines I set out between buildings, so we aren't just dropping straight down to the street.  But it's elastic, and I can't account for how much stretch there'll be in the material.  Or how much stretch won't be there.''



``And if he's got gunmen, too?  We're left there dangling out over the middle of a street?''



``It's one option,'' I said.  ``One.  We'll have your darkness so they won't necessarily have clear shots.''



``And you have your bugs,'' Regent said.



``Our opponent here knows \emph{exactly} what we can do.  He's worked with us and observed us for weeks.  Excepting Imp and I, he's worked with you guys for \emph{months}.  Over a year.  So no, he's not going to do something like underestimate the range of my bugs.  He's going to have snipers that are just beyond my usual range and I won't be able to fight back.''



``Your relay bugs?''  Regent suggested.



``Dying.  But yeah, I'll bring them out.  I suppose a night like tonight warrants using up the last of their reserves.''



``And you can fly,'' he said, pointing straight up, where Atlas was in the skyline, circling around a stationary Shatterbird.



``I can, but I'd almost rather use the cords and swing down to the street level.  If I'm flying and they get a lucky shot off, I'm pretty fucking screwed.  They hit me, Atlas won't ease me to the ground.  They hit Atlas, nothing I can do to stop falling.  Besides, being on the ground means I have the utility Atlas brings to the table.  Being mounted on him means he and I are essentially one unit.''



``I think you're overthinking this, dork,'' Regent said.



``No,'' Grue and I said together.  Grue didn't say anything more, but I added, ``We plan for every possibility and we're wrong?  We don't lose anything.  If we plan for a situation that \emph{does} come up?  We'll be glad we did it.''



``You're going to drive yourself insane worrying about it,'' he retorted.



``If she hasn't already, I don't think she will in the next ten minutes,'' Tattletale said.  ``You sense them on the ground, Skitter?''



I shook my head.  ``My power's radius is like a bubble, and the bottom end isn't covering that much ground.  I should have been waiting at a spot lower in the building.''



``They're on their way up.''



I could sense them as they reached the base of the building.  Thomas Calvert would be the man who led the way, and the men who followed him were outfitted in PRT gear.



It took time for them to ascend.  The building was only partially complete, with floors, some walls and the steel skeleton of beams with tarps stretching between them for the remainder, but no elevators.



Without discussing it, we arranged ourselves on the rooftop, preparing to meet them.  I was a little surprised that Grue and Tattletale positioned themselves so they were each just a little behind me, with Imp, Bitch and Regent behind \emph{them}.  Bentley prowled at the perimeter of our group, three-quarters of the way to his typical `monstrous' size and slowly growing.



Thomas Calvert was the first to cross the threshold.  Annoying that the first time I would `see' Coil unmasked, I would be blind.  He waved one hand to brush away my bugs as they passed over him, but I managed to pick up the essential details.  Close cropped, coarse hair, trimmed eyebrows, thin lips and a cleft chin.  He wore the body portion of a PRT uniform with an insignia stitched onto his sleeve that I couldn't make out with my swarmsense.



Most of the squads remained below, but he was joined by a handful of soldiers and three young men in plainclothes, one of whom looked like a bodybuilder.



``Yo, Frenchy,'' Tattletale said.  ``Sup?''



One of the uniforms nodded a slight response.  Was he backed up by a `PRT' squad or two consisting of his hired mercenaries?



``Undersiders.  After your last interaction with Director Piggot, I assumed you would want to speak to me and try establishing ground rules?''



``We know it's you, boss,'' Regent said.



My bugs caught the slightest exhalation from Director Calvert's nostrils, a minor expression of annoyance.  ``The Travelers were a little more circumspect.''



``Circum-what?'' Imp asked.  I couldn't tell if she was genuinely wondering or if she was being intentionally obtuse.



``Tone it down, guys,'' I said.  \emph{They're the types to go after any weakness in authority figures.  They'll nettle him until someone gets in trouble}. ``Director Calvert.  Would it be too much to ask for you to ask your squad to wait downstairs?''



There was an extended pause before he offered a slight nod to one side.  His squad turned to return downstairs, and I followed them as they took position by the base of the stairwell.



``I asked you to stay out of costume until further notice,'' he spoke.



``With all due respect, Director,'' I said.  Tattletale had coached me; I would stroke his ego by reinforcing his new position.  ``I was injured as a bystander in Coil's attack.  I wouldn't have been hurt if I'd been costumed.  Until everything cools down, I think my team and I will play it safe.''



``I see.  I can respect that.  Nothing serious?''



``Serious?  Yes.  But it's nothing life threatening and nothing that can't be fixed.''



Thomas Calvert reached beneath the armored panel of his vest and withdrew a small remote.  He stared at it for several long seconds before putting it away.  That done, he clasped his hands behind his back.  It was a position that was very `Coil'.  It was obvious and direct enough that I suspected he was dropping his Director persona and admitting his true nature.  ``My apologies.  I am not infallible.''



\emph{You let a dozen or more people die and left twice that many people injured in some way.  No, you're not infallible.}



I kept my mouth shut.



``I just checked for listening devices.  You aren't recording this, which means I can answer any questions you have.''



``How much of that was planned?''  I asked.



``More than you might suspect.  Every person in that room who was not in the audience was accounted for.  Mr. Grove and Mrs. Padillo were selected and recruited well in advance.  Circus and Chariot were hired nearly a year and a half ago, their actions and development in the public eye carefully orchestrated.  \"{U}ber and Leet were recent acquisitions.  I needed a heavy metal suit that could carry a package, and Trainwreck died at an inconvenient time.  Most reporters were selected and stationed well in advance, claiming the rear of the room where they would bear the brunt of the attack, so to speak.''



``They didn't die?'' I asked.



``As with Circus, \"{U}ber and Leet,'' Director Calvert nodded in the direction of the three individuals in civilian clothes.



``Wait, Circus is a guy?'' Regent asked.



``Depends on your definition of guy,'' Tattletale said.  ``If you're talking biological or what Circus identifies as.  Not that I have it pinned down; I can't tell if you're a guy posing as a girl when in costume or a girl who poses as a guy when in plainclothes.''



Circus spat, directing a loogie to shoot a horsefly out of the air.  ``I'll take that as a compliment, I guess.''



``The three of them and most of the reporters were removed from the premises in time,'' Coil said.  ``The reporters, as I said, were plants.  I needed news reporters in place who would be sure to catch the details I wanted them to catch.  Some editing of the footage just prior to it being sent to the news stations served to smooth rough edges and highlight key points.''



``Making Piggot look worse, for example,'' Tattletale said.



``Among other things.  Appearances are one of the most important things, here.  With Chariot's help, we created a rough emulation of Trickster's power.  The reporters were swapped out, a sufficient amount of raw biological matter was swapped in.''



``\emph{Human} matter?'' I asked.



``That is what the paperwork will say, which is the most important aspect,'' Director Calvert answered me.  ``Rest assured, no serious harm was done.  Circus' abilities allowed us to place the knives in nonlethal areas.  Better that Director Piggot looks as ineffectual as possible than simply perish.  The same applies to the mayor.  Thomas Grove and Mrs. Padillo will recover, but Thomas Grove will concede the election, supporting Mrs. Padillo, despite his strong showing.  It will help shake the notion that things were staged.''



``But they were.  Every part of it,'' Tattletale said.



``Every part of it.''



``The bomb?'' I asked.



``The sabotaged power supply was real, but \"{U}ber's metal suit housed a teleportation apparatus to detect when it was removed from the premises, so a replica could be brought into the lobby.  The initial detonation was little more than light and a shockwave primed to make the most of the Manton effect, leaving my agents with little more than bruises and scratches.  They were teleported out, as I already said, just before the final, \emph{true} detonation.  We estimated how fast the evacuation would proceed and calculated a blast radius that would leave the building standing and the crowd largely untouched.''



I could remember Tattletale mentioning how there were less killed or injured than I might have thought.  Had she guessed this much?



``Every action I've carried out has been carefully weighed, with attention given to the \emph{aftermath}.  Circus, \"{U}ber and Leet will be leaving Brockton Bay with a sizable reward for their efforts.  I don't expect they will need to return to a life of crime, but I believe they will use a different identity and modus operandi if they do?''



He'd made it a question, and \"{U}ber answered, ``Yes, sir.''  I could feel Leet and Circus nodding.



``Good,'' Director Calvert spoke.  To us, he said, ``It just isn't worth killing good help.  Should my ultimate plans here fall through, it's better to have individuals like them on reserve.''



``And us?'' Grue asked.



``Your part in Brockton Bay isn't entirely over, yet.  I established you here for a reason.  As Director, I will lead a slow but successful campaign against Brockton Bay's villains.  The Travelers will be the first.  I expect a strike squad of my PRT agents will catch them off guard, but they will ultimately escape capture.''



``How unfortunate,'' Tattletale said.



``Indeed,'' Director Calvert replied.  ``Doubly unfortunate if other villains should establish a presence in Brockton Bay's south end, forming a loose alliance with the Undersiders, who maintain a firm hold on the flourishing North end.  Oh, rest assured, you Undersiders will lose your hold on this city over the course of months, but it won't be quite as bad as it sounds.''



``We'll avoid being captured, probably,'' Tattletale said, ``Or we'll get captured and break out before there's an issue.  And then we don't come back to Brockton Bay.  We wind up establishing presences in nearby cities.  One or two Undersiders with a firm grip on a given city with other villains under us, establishing a new kind of villainy, and you, Director, as the valiant hero on the opposing side.  Your power grows in a way the public is very much aware of, and, well, \emph{we're} not losing quite so much as it seems, so your power grows in other ways too.''



Thomas Calvert spread his hands, ``It seems you have a firm grasp on what's going on.  I won't waste our time reiterating.  Any questions?''



``Why become PRT director?'' Grue asked.  ``Why not mayor?''



``All eyes will be on the mayor after the recent fiasco.  Mr. Grove will serve as a red herring, drawing all suspicious eyes to him before he defers the election to Mrs. Padillo.  Besides, who would you rather rule?  A dozen capes or fifty thousand unpowered civilians?''



``I see,'' Grue said.



``The fear this event creates among the public will make requisitioning additional capes and resources that much easier.  The remnants of Coil's personal army will remain in the city, a sub-gang of highly trained individuals who will serve as an excuse for why the forces of the Undersiders do not grow beyond a certain point.''



``You said the Travelers will be the first to be ousted,'' I said.  ``Does that mean you've found a solution to their problem?''



``No.  But we have several last resort answers, and those will be exhausted soon.''



With my bugs, I noted Tattletale making a hand gesture.  Left index finger and middle finger pressed together, she tapped her thumb against the tips of the other two fingers.



``Any other questions?'' he asked.



``Dinah,'' I said.



``Mr. Grove's concession to Mrs. Padillo will involve an offer.  He will push for his constituents to support Mrs. Padillo if she accepts his terms.  Among these will be a restoration project for the North end, employment stimulation for the laborers and a restoration of the ferry service.  In exchange for your continued cooperation, I can give you executive powers in naming the measures you'd like to see pass.  I am well aware of what I agreed to, but I would offer this as a compromise in exchange for a one year delay on that term of our contract.''



``No,'' I told him.  ``I'm sorry, but you've got to let her go.''



``Then I will.  I'm disappointed, but I won't have it said that I'm not a man of my word.''



My heart was pounding.  \emph{Just like that?}



Director Calvert clasped his hands in front of him, ``How would you have us resolve this?  I can return her to her family, or pass her on to your custody.''



\emph{I didn't think this far ahead}.  ``Her family, then.''



``Very well.  With your permission, we'll release her to her parents, with some covert surveillance to ensure she does not reveal any details of my greater mission.''



``Okay.''



``My officer will take you to her.''



I hesitated.



``Your teammates can join you, if you don't feel secure.''



Grue placed a hand on my shoulder.



``Thank you, Director,'' I said.  ``I don't mean to impugn your sense of honor, but I didn't expect this.''



``I have a healthy respect for paranoia, Skitter.  Go.  Tattletale, could I borrow a few minutes of your time?  The Travelers grow anxious, and you can offer some more answers about Noelle's situation.''



Tattletale turned our way, ``Your call, guys.''



``Take Regent and Shatterbird with you,'' Grue said.



``You sure?''



``If he respects paranoia, he'll respect the fact that I'm as worried for your well-being as I am for Skitter's.''



``Aw,'' Tattletale gave Grue a pat on the cheek, ``You're not a very good liar.  I appreciate the sentiment, though.''



I felt entirely out of my element.  For weeks, months, I'd been bracing myself to hear Coil say no.  To hear him say `I promised I'd \emph{consider} it' or `I promised to release her when my plan reached its conclusion, and that won't happen for another year.'  I didn't know what to do with my hands.  If I'd had pockets, I'd have jammed them in there, but I didn't.  My belt didn't really suit itself for me hooking my thumbs in there.  I didn't even trust myself to speak, with the possibility that I could say something to ruin this.



No, it was better to be on my guard.  I swept the area for threats, with bugs on every set of gloved hands and every weapon.



But the PRT uniforms climbed into their vans and the doors slammed shut.



Director Calvert stayed at the gates that marked the construction site from the roads beyond, Tattletale and Regent beside him.



``In the truck,'' the remaining PRT officer told us.



``If it's alright,'' I said, ``We'll ride.''



He looked to Coil, who nodded.



I climbed onto Atlas, and Grue settled behind Bitch on Bentley.



It was a fifteen minute flight, following the truck, and I was on edge for every second.



We stopped outside of a brick building, and the driver of the truck stepped out.  I swept the area with my bugs, then swept it again.  The interior featured modest living accommodations, a squad of armed soldiers, a man who wasn't armed and a little girl.



I set Atlas down and waited outside, bugs poised to attack.  The door opened, and the soldiers stepped out, parting to let Dinah go free.



The little girl stepped out, hesitant, then stopped.  Nothing gave me any indication that she was unhealthy or hurt, but she wasn't \emph{lively }either\emph{.  }She was dressed in a skirt, sweater and uggs, her hair thick with chemical smells that told me it had been recently washed.



``Want to go home?'' I asked.  I reached out.



Her hand found mine, and I clutched it tight.



Couldn't leave on Atlas.  I turned, and she stepped to follow.



Through my bugs, I could feel the thrum of the truck as it started up, I could feel the mild heat and see the flare of light as the highbeams shifted on.  If I could see, they would have been blinding.



I tried to squeeze Dinah's hand, to reassure her, and found myself clenching an empty fist.



My bugs weren't where they were supposed to be.  I was momentarily disoriented as I tried to map my surroundings.  When I felt hardwood beneath my feet, I scattered the bugs from beneath my costume.  Containment foam, all around me.  I'd been teleported.



And Calvert.  Calvert and a squad of his people.



``You bastard,'' I said.



There was no response.  I could feel how his arm was outstretched, sense the general shape of the weapon in his hand.  The others had weapons too.  I could attack, but it would only make them open fire.



``No monologue?'' I asked, ``You're not going to explain how you did it?  How you're going to deal with my teammates or explain what happened to me?''



He answered with a pull of the trigger.





