





I'd sensed the movement of his finger a fraction of a second before the gun went off, and tried to lean out of the way.  It didn't help.  Dodging bullets wasn't a trick I had my repertoire.  Judging by the way the gun followed me as I moved, Thomas Calvert either knew his way around guns or he was using his power to help ensure he hit his target.  Or, more likely, it was both.



Getting hit, the smallest part of me could only think \emph{costume }\emph{can't stop a bullet after all.  }Except it wasn't even a complete thought.  Just a momentary disappointment as I felt the impact of the bullet passing through my chest to my back.



I hit the ground, my mouth agape, and I couldn't feel my heartbeat in the aftermath of the hit.  It felt like a sledgehammer had hit me in the dead center of my torso.  I couldn't speak, couldn't even \emph{think }in a coherent fashion.



But the remainder of my bugs were already flowing out of my costume as I fell prone.  Capsaicin bugs moved in the general direction of Thomas Calvert and his soldiers, pre-prepared cords of thread unspooled from beneath my costume, trailing behind flying insects.  I couldn't think straight enough to orchestrate a smart attack, to tell them to go for the weak points, but they advanced swiftly, biting exposed flesh and forming a barrier between me and my attackers.



Calvert backed away, his nose and mouth tucked into the crook of his elbow, eyes squinting shut.  He emptied his clip in my general direction, but he didn't have a bead on me.  He couldn't see, between the cloud of bugs between us and the bugs crawling on his face.



I had flying insects catch the end of his gun with a cord and pull it off target further, and he backed up.  I went a step further and wound threads around other guns, hoping to forestall the inevitable onslaught of bullets.  If I could find leverage, someone or something that was moving, and pull them off-target before they shot me down-



When he spoke, his voice was raised to be heard despite the muffling effect, ``Out of the room.  Fill it with bullets\ldots no.  Scratch that.''



\emph{He's coming up with counter-counter-plans before I even have a strategy in mind.}



``\ldotsSet her on fire.  Her costume is bulletproof, and I want this \emph{done.  }I need to attend to other matters.''



I couldn't breathe.  I could exhale, was huffing small breaths of pain, but I felt like my chest had caved in.  My pulse wasn't pounding, my blood seemed to move too slowly through my veins, and I couldn't inhale to inflate my crushed chest.



Through my bugs, I could sense the two men stepping forward.  Each wore gas masks and each had a bottle in one hand.  A pungent odor trailed behind them, overwhelming and oppressing my bugs' senses of smell and taste.



I pressed one hand to my chest, as if I could gauge the damage done, and reflexively pulled it away as I touched something hot.  A snarl of metal, embedded in the thickest portion of the armor I'd designed into the chest, and it was hot enough that it hurt to touch it.  \emph{A bullet,} I thought.  \emph{I'd never considered that bullets would be hot}.



The realization coupled with the sting of the burn at the base of my palm helped to clarify my thoughts.  The bullet hadn't penetrated.  I'd felt, what, the shockwave of the bullet hitting?  Or I'd filled in the blanks wrong in the \emph{expectation} of getting shot?



It didn't matter, because one of Thomas Calvert's soldiers had just flicked the switch on a lighter, and I realized the bottles they were holding had to be makeshift molotov cocktails.



Though my body was numb and my responses felt too sluggish, I reached behind my back.  With some of the non-flying bugs still residing in my utility compartment, I found what I was looking for in a flash, drawing it from the slot I'd dedicated to it and getting it in position in my hand in an instant.



I aimed the pepper spray at the lighter and fired.  It offered ten feet of range, and they were on the other side of the room, with a heaping mess of containment foam between us.



The pepper spray ignited and set fire to his sleeve and the shirt around his upper body.  The lighter dropped to the ground as he thrashed, trying to pull his shirt off despite the gloves and the gas mask he wore.



It wasn't the brightest move, trying to stop someone from lighting a fuse by setting them on fire, but I wasn't in a position to be picky.  I tried to push myself to my feet, but my chest flared with pain and I collapsed, putting me in a position that was almost worse.  The pain lanced throughout my ribcage, as if the structural integrity wasn't there, and putting any strain on my torso threatened total collapse of everything that held it together.



My bugs were already moving towards the other guy with the molotov.  He'd hesitated at seeing his buddy go up in flames, and now cords of thread were winding around the neck of the bottle, the fingers that gripped it and his wrist, entwining them.



``\emph{Irritating,'' }I was aware of Thomas Calvert's voice in the next room.  He'd retreated and shut the door behind him, but it burst open as the man with the molotov tied to his hand beat a retreat before it could be ignited by the still-thrashing man.  Calvert added a snarled, ``Damnation.''



``If we use grenades--'' one of the soldiers started.



``Do \emph{not} use grenades.  I assure you it does not work out the way you imagine it will.  Give me that.''



I could sense Director Calvert tearing the bottle free of the man's hand.  I began arranging my bugs, creating a loose net with threads.  It wouldn't stop the forward momentum, but I had some cord left.  I began winding it around the light fixture on the ceiling.  If I could catch the bottle-



He didn't do as I'd expected, he didn't light the rag, for one thing, and he didn't toss the bottle at \emph{me}.  Lobbing it underhanded, he tossed it at the floor just past the door.  The bottle shattered and the contents, gasoline by the smell of it, spread across the other half of the room.



The burning soldier that was still in the room with me screamed, yelped out the word, ``No!''



He made a break for the door, and Calvert shot him.  The bullet wasn't enough to stop the soldier's forward momentum, but one of the other soldiers kicked him hard in the stomach.  Calvert used his foot to push the door closed as the man fell onto his back, landing in the pool of gasoline and broken glass.



His still-burning clothing ignited the accelerant.  In a heartbeat, the floor in front of the door was on fire, and the room was filled with the shrill screams of the thrashing, burning soldier.



I experienced a moment of animal panic.  The kind of mindless fear that was hardwired into our brains on a basic level, so that we, like a wolf, a deer or an ape would, knew that fire was \emph{bad.}  Smoke was bad.  Fire was a thing to run from and I had nowhere to run.



I shook my head.  Had to think.



There was one exit to the room.  To get to it, I'd have to leap over a heap of containment foam, which I wasn't sure I could manage with the way my chest was hurting and with no real running start.  Even if I passed the hurdle -and failure would mean I was stuck and trapped- I'd have to run through a pool of burning gasoline, avoid tripping on the flailing, burning man, get to the door and pull it open.



Except Calvert was calmly, efficiently ordering his men to gather tables and chairs and stack them against the door, as if the fire in the next room wasn't even a concern.  A chair was propped up so it was under the doorknob, a heavier dining room table blocked the door itself.  Three soldiers worked together to move a tattered sofa, lifting the end to put it on the table.



My bugs.  I didn't have enough here in the building, not enough to mount a serious attack on Calvert.  Most of the ones I'd brought with me had burned up as the room caught fire.  Some clung to Calvert and his men, but they were too few to do more than hurt and annoy.  In my mindless fear, I'd called for my bugs to come to me.  Or my passenger had, perhaps.  Maybe it was the two of us, working together through my subconscious.



Either way, I had only a few \emph{usable} bugs, a whole mess of useless ones like moths, houseflies, cockroaches and ants from the surrounding neighborhood, and Thomas Calvert, \emph{Coil}, was on his way out of the building.



I looked at the bigger scene.  I was in one of the areas that had been abandoned when Leviathan attacked.  This house hadn't been nice to begin with, and the flooding had made things worse.  Calvert had prepped the area prior to teleporting me in.  The house sat on the corner of the block, and the two neighboring houses had been bulldozed.  There were no people in range that I could see.  He would have cleared it out so there were no eyewitnesses.  Portable chain link fences had been put up and bound together with loops of chain at the perimeter of the property.  He was stepping through an opening now, and his men closed it behind him, threading chain through.  Going by the lock one soldier held in his hand, they clearly planned to lock it as they had the others.



Just past the perimeter of the fence, there were a dozen trucks and cars surrounding the building, each turned toward the property, their headlights on.  Squads of soldiers stood beside and in front of the trucks, guns raised and ready.  Most had machine guns or handguns, bandoleers of grenades and all-concealing body armor.  Three had containment foam dispensers.



Leaving the property would be impossible, which didn't matter because I wasn't capable of leaving the \emph{room}.  There were two windows, only one of which I could reach, and both were boarded up.  Not even just boarded up against the window frame, but the planks of wood were long and fixed to the studs of the \emph{wall}, too.  I ran my hand over the end of one plank and felt the raised bumps of nails or screws.  An ant climbed off my fingertip to move over the surface of one bump.



Screws.  Screws with \emph{hexagonal slots}.  Because Calvert wasn't willing to risk that I'd have a screwdriver on hand with a more typical head on it.



I laughed.  It made my chest seize up in pain, it probably sounded a little crazed, but I laughed.  It was too much.



This would be a perfect time for a second trigger event.  Hadn't Lisa said that my mind-power link was enhanced whenever I felt trapped?  I doubted I'd ever feel more trapped than I did right this moment.  I couldn't see just how far the fire reached, because I was \emph{blind}, and the heat of the fire was killing the bugs I needed for sensing my surroundings.  I had only a minute or two before the room became an oven and killed off the rest, leaving me blind and roasting to death.



I coughed as a wave of smoke hit me, and ducked my head low to keep breathing.



No, I probably wouldn't burn to death.  I'd suffocate as the flame ate up the oxygen, go out quietly before I started burning.  Maybe I'd trigger \emph{then}, after things got that bad.  It wouldn't help, probably.  I couldn't think of a single permutation of my powers that would get me out of this mess.



I went on the attack, sending my bugs after Calvert and his people.  Too many were useless, many weren't even capable of \emph{biting.  }Still,\emph{  }I found three black widows in the immediate area.  After a moment's consideration, I delivered them straight to Calvert.  They found flesh at his neck and bit.



He swatted at them, pinched one between his fingers, and raised it in front of his face.  Then he said something I didn't catch.



There was no hurry in his movements as he flicked the dead spider to the ground and called out an order to his men.



The order, I feared, I actually heard and understood.  It helped that I had enough context to guess what the words were and fill in the blanks.



\emph{Burn it to the ground}.



``\emph{Fuck you},'' I whispered, pressing my hands to the wooden planks.  I coughed as I inhaled another waft of smoke, then coughed harder as the combination of the pain in my chest and the smoke I was inhaling in my attemtps to catch my breath made for a self-perpetuating cycle.  Calvert's men were lighting more molotovs, tossing them over the fence they'd erected.  One hit the side of the building.  Another hit the front porch.  Three or four more hit the lawn and surrounding property.



Calvert glanced over his shoulder, then confidently strode over to a car and took a seat in the back.  He didn't have the driver take him away.  No, he'd be more interested in \emph{watching}, in verifying that things went according to plan.  Putting himself in the car meant only that he was out of the reach of my bugs.



Not that he'd seemed concerned about the black widow bites.



Chances were good he'd already taken the necessary antivenins.  Damn it, and the antivenin that worked on black widow spiders also worked on any number of \emph{other} spiders.  He'd probably suffer side effects, but that wouldn't be immediate.



I had to refocus.  The one in immediate peril here was \emph{me}.



I considered waiting for the fire to weaken the floorboards before leaping over the foam and plunging down to the lower level, then dismissed that idea.  I wouldn't last that long, for one thing, and there was too much chance of me being injured.



There was only one real way out of the room, and that was the window.  I'd have to ignore the men stationed outside for now.  I considered using my knife to try to pry the board free of the wall and the frame.  I doubted I had the strength, with my chest hurting like it was, and I doubted I could pry enough boards free in time.  He'd put three screws in at each point of contact.  Hell, I had suspicions that Calvert had considered the knife when he'd ordered that the windows be boarded up.



I drew my gun.  I wasn't sure how much information Calvert had, but he hadn't seemed to care about the possibility of me opening fire on him while he'd been here.  That, or he figured his power would give him an out if he happened to get shot in one reality.



It was hard, not just moving and aiming the gun while I was coughing and still reeling from the hit to my chest, but aiming at the targets I needed.  I had only so many bullets, and there were too many planks to use several bullets to remove each one.  No, it was better to angle the shot so I was hitting more than one plank at once, both the ones that had been nailed up on the outside of the building and the planks inside the room.



The recoil of the shot was so fierce that it made the pain in my chest flare up.  I dropped the weapon, suppressing coughs.  Even behind the lenses of my mask, my eyes were starting to tear up.  Not that it particularly mattered, given how I couldn't see, but it was one more distraction.  Bending over redoubled the pain and brought me to the point where I nearly collapsed, coughing to the point that I was seeing spots.



The floor was warm enough that more sensitive bugs were dying as they touched it.  Finding where I'd dropped the gun was a combination of guesswork, fumbling with my hand and using more durable bugs to feel it out.



I picked it up and shot twice more.  Fighting the pain in my chest, I reached up and pulled down on a board.  It was splintered in three by the gunfire, two on the left and one on the right, and I managed to use my body weight to get the necessary force to tear it free.



Three more bullets and I was able to remove one more from the inside.  I used the removed board and wedged it into the crack between the two boards on the far side, leveraging one free.



The gunfire had attracted attention.  Someone called out an order, and a dozen machine guns pointed to the window.  I went low, hiding not at the base of the window, but near the corner of the room, lying with my feet pointing towards them, my hands over my head, all too aware of the flames on the wall, within arm's reach.



Bullets punched through the exterior walls and interior walls both.  One clipped through the floor to hit the armor at my back.  The impact prompted another coughing fit, worse than any of the ones before.



I needed to get out, and soon.



They \emph{knew }I needed to get out, and they weren't giving me the opportunity.  There was a momentary pause as the soldiers ejected magazines.  Or clips.  Whatever I was supposed to call them.  Guns weren't my thing.  They replaced the clips and opened fire with another barrage.



I couldn't lie there, waiting for one to get lucky and hit me, for the smoke to get to me, or for any of the other possible fates I faced.



My bugs had gathered around the exterior of the building, called to me by my power, clinging to the roof and outside walls near the room.  I took note of the cockroaches, then directed them to the trucks that had the building surrounded.



Cockroaches retained the ability to eat virtually \emph{anything}.  I could have used more, but I'd have to make do. They began eating through wiring.



My own situation was getting bad, now.  The floor was quickly going from warm to \emph{hot}.  The containment foam was stopping the spread of the fire across the floor, but it wasn't stopping the progression of the flames beneath the floorboards.  If the floor caved in beneath me, I'd be as dead as anything.



Commands went out, and the soldiers switched to firing at me in \emph{shifts}, only a few firing at a given time while the others stood at the ready.  It made for a relentless, unending barrage.  The second shift was just starting up when the first of the headlights went out.  The cockroaches had found the right wires.



As the truck headlights started flickering out, I commanded my bugs to gather at the base of the window.  No less than five bullets tore through the mass as the bugs collected.  The soldiers had only the light of the fires to go by, now, and they'd spotted the anomaly at the window.



The lump of bugs dropped to the ground, and more bullets penetrated the heap that landed at the base of the building.  When the bugs rose, they rose in the general shape of a person, of \emph{me}.



I desperately wanted to be out of the room.  I was coughing more than I was breathing, and I worried that the next serious coughing fit would see me blacking out before I sucked in enough oxygen.



But I had to wait.  I gathered more swarms and dropped them from the edge of the window.  Every bug in a three block radius contributed to forming decoys.



Each decoy, in turn, had to act like it was sustaining gunfire.  They moved slowly, stopping when the bullets hit, some flattening out to mimic falling to the ground.  It made for slow progress as they advanced to the fence.



I couldn't stand to wait any longer.  I knew I should make one or two more decoys before going ahead, but the conditions of the room were going from unbearable and dangerous to \emph{critical}.  I approached the windowsill as the next mass of bugs gathered, submerging myself in the midst of them, my hands on the window frame.  I tried peeking through, but my hazy, ruined eyesight only offered me a glimpse of one blot where a single truck far to my left had a working headlight.  I faced a small army; I was about to drop two stories to what had once been someone's garden, now a muddy mess of dirt and detritus, and-



One bullet hit me in the forearm, not too far from where Brutus had bitten me, months ago.  I slumped onto the windowsill, cradling my arm.  More out of desperation than anything redeemable, I forced myself forward between the broken planks and let myself drop to the ground below.



The landing wasn't as hard as it could have been, but it wasn't gentle either.  I was left writhing, dry heaving, much of my attention on keeping from screaming in pain and keeping the bugs all around me.



I used all the residual willpower I could manage to turn over, putting my back with the armor of my utility compartment and the added fabric of my cape towards the ongoing gunfire from Calvert's personal army.  I covered the back of my head with my hands and fought the urge to cough.  I doubted anyone would hear if I did, with the constant gunfire and the sound of something collapsing inside, but I couldn't risk a coughing fit that left me blind to my surroundings or passing out.



Now I was left with the task of passing through the perimeter.  One of my swarm-decoys had reached the fence, and was apparently doing a good enough job of selling the \emph{possibility }that it was me that they felt compelled to double-check with the occasional burst of machine gun fire.  I commanded it to start climbing.



I had six decoys now, with another in progress at the window.  I'd planned to crawl, to get to the fence and find my way through, but with my wrist like it was\ldots



One of Calvert's men lit another molotov and tossed it at the base of the fence where the decoy was climbing.  It was obliterated in an instant, and Calvert's men were forced to back away from the resulting bonfire.



If Thomas Calvert was using his power to guide his men, to give them an advantage and give them directions that would help narrow down the decoys, then I'd inevitably face the same fate as the decoy had after I got to the fence.



But he wasn't giving directions.  He was in the truck, watching.  No radios were sounding with instructions, not yet.  He had to protect his perimeter, keep me from getting to freedom\ldots but he was in a reactive position, not an offensive one where he could command an attack and then make it so it never happened if the attack went awry.  No, I'd weathered that initial attack.



I wasn't sure exactly \emph{how} I'd weathered it, but I had.



I crawled with three limbs, while my decoy formed a standing figure above and around me, then I joined the other decoys that were advancing on the fence.



Another molotov sailed over the fence to strike the lawn on the other side, incinerating one decoy that had ventured too close.  Again, I noted, the soldiers backed off.



That wasn't entirely a bad thing.  The more they backed up, the thinner the defensive lines were.



But I still needed to get to the fence and get \emph{over} it without getting shot or set on fire.



I still had more bugs arriving from the extent of my range.  Being trapped like I had hadn't given me a second trigger event.  I wasn't so lucky.  But it had extended my range.  I tallied the resources I had at my disposal, considered how many more decoys I could create\ldots



Then I reconsidered.  No, I needed a distraction, and these slow-moving decoys weren't that.



The bugs I still had in reserve swept into the ranks of the soldiers, and I went flat for my own safety, covering my head.



\emph{``Behind you},'' one collection of bugs whispered to a soldier, my swarm-speak forming the necessary words.  He whipped around to see nothing there.



\emph{``I'm going to eat you alive},'' another swarm spoke, somewhere nearby.



``\emph{Crawl inside your body and lay eggs}.''



Calvert's voice sounded over a dozen radios in the area, ``She's playing mind tricks.  She's still near the house, and she's never killed or tortured before.  Maintain the perimeter and do \emph{not} use grenades.''



Again, with the refusal on the subject of grenades.  A \emph{reminder,} even, this time.  Was this a point where he'd split the timelines, bombarded the house with grenades in one reality and stuck to the guns in another?



Or had he already verified that I had a counterattack in mind for the grenades?  He could have employed them in an earlier scenario and had things go catastrophically wrong on his end.  There had to be a reason he wasn't using them instead of molotovs.  Grenades would have been faster, given more immediate, definite results.



Then there was the possibility that this tied into his alibi, that he didn't want the Undersiders or even the Travelers to know he'd gone after one of \emph{them}, and the use of several grenades would be too easily traced back to `Coil'.  He would stick to an over the top arson, maybe hide the police reports and suppress the media.  If I was in a territory owned by the Travelers, maybe they'd accept a price for keeping this quiet from the Undersiders.



Or any combination of those things.



Then I remembered how I'd escaped from the hospital bed after the Endbringer attack.



The bugs continued whispering as they went on the attack, but their attack wasn't a headlong rush with stingers and pincers.  As I lay flat on the ground, arms shielding my head, I took a different tack.  I \emph{raided}.



Bugs swept into pockets and pouches, searching the contents.  First aid supplies, no.  Gun magazines, almost too heavy.



I noticed the bandoleers of the grenades that Calvert had alluded to.



The decoys had forced the enemy to spread out gunfire.  The soldiers were further diverted as my bugs tried to divest them of possessions, pushing at the gun magazines and attempting to slowly nudge them free of pouches.  Spiders wove silk cords, and I chose my target, a soldier by the fence, between me and Coil.



Long seconds passed as bullets hit the earth only a short distance from me.  I waited, \emph{prayed} that the next thrown molotov wouldn't land near me.



At my instruction, flying bugs carried a cord out, connecting a grenade on his bandoleer to the fence.  Another connected the same grenade's pin to the soldier next to him.



``\emph{Lose the grenades},'' my swarm buzzed, right next to him.  ``\emph{I'm pulling a pin}.''



The man next to him heard, stepped away, and the cord went taut.  The pin slid free.



He had the grenade free in a second, but he simply held the bar at the side of the grenade down.



\emph{Damn}.



``\emph{Think fast.}\emph{Pulling two more,}'' my swarm spoke.  A benefit of speaking through the swarm was that it was hard to hear a lie in the tone.



He realized that he had only the two hands to hold down the bars for three grenades, and tossed the one in his hands towards the house.  The cord connecting it to the fence halted the grenade's trajectory and it swung straight down into the waterlogged lawn on the far side of the fence.



When it detonated, it ripped through a section of fence and sent soldiers scattering for cover.



\emph{Be patient}, I thought.  I could have made a run for it then, but there was no use.



``She's pulling the pins!'' the soldier who'd been near my target shouted.



They began retreating, and the defensive line thinned out further.  Some soldiers were standing on the far side of the \emph{neighboring} property, now.



``Need a visual!'' someone shouted.



A flare sailed through the air to land on the lawn, fifty feet to my right.  The light it provided would let them see through my decoys.  If they put one too close to \emph{me}, they'd see my silhouette.



More sailed my way, and I set to moving them before any landed too close to me.



I maintained the pressure, an indiscriminate attack that Calvert couldn't necessarily counter.  I repeated the process, roughly, that I'd used to get the one soldier to throw a grenade, aiming to knock down the fence on the opposite side of the property.  I made the cord tying it to the fence too thin, however, and the grenade landed closer to the base of the house.  The fence remained standing, but the soldiers backed away in the face of the dust, smoke, and hot air that billowed out from within the building.



``\emph{I'm pulling your pins next.}''



``\emph{Crawl up your asshole and leave you some tapeworms.}\emph{``}



``\emph{I'm behind you.}''



``\emph{I can have centipedes crawl beneath your eyelids.  Chew your eyes out at the root.}''



``\emph{Ever wonder if a mosquito could pass on the H.I.V. virus?}''



The psychological pressure was important, too.



``\emph{Do not throw the grenades,}'' Calvert's voice sounded over the radios.



The drawback of the psychological pressure was that many soldiers were now shooting indiscriminately at the property, and I didn't have anything even remotely resembling cover.  I began belly-crawling across the grass, using my one good arm and my knees.



I felt an impact across my face.  The briefest shriek escaped my lips before I remembered to clam up, managed to convince myself that it was only a clod of grass and dirt that a stray bullet had kicked up.



Someone had heard.  A female soldier, she was on the other side of the fence, not five feet in front of me, and her head had snapped in my direction as I'd let the sound escape.



I barely had any of the pre-prepared silk cord left.  I split the swarm around me into two, and sent one to my left.  The soldier held her machine gun in one hand and fired at the running swarm, drawing a flare with the other hand.  In the meantime, I was getting my feet under me, lunging.



Dragonflies carried the silk cord between the wires of the fence.  I didn't go for the grenades on her bandoleer, but the can at her waist.  They circled the pull-tab, and I held the other end of the cord, pulling.



My first guess was that it was a flashbang, in which case it could leave my bugs stunned and me exposed.  My second guess was that it was incendiary, in which case I'd be murdering someone.



When it went off, I felt only relief.  Smoke billowed around her as she called out to others, telling them I was near.  I sensed her backing away, getting the canister free of her belt and tossing it aside, and had my bugs collect it and cart it her way.  I crawled in the direction she \emph{wasn't} walking, using my power to identify where the soldiers were moving and using the smoke for cover.



Scavenging used silk from previous attacks, my bugs arranged to pull more pins for smoke canisters.



The end result was chaos.  It was the best result I could hope for.  With the smoke at the open area of the fence and the possibility that I had climbed over where the smoke masked things, they couldn't be sure of my location, and they couldn't shoot into the midst of their allies, so they were forced to retreat further.



I sensed Calvert's truck pulling away.



Calvert could use his power to prune away possibilities that didn't work for him, but only if he was aware of me, aware of my movements and how I was mounting my attack.



His retreat left me wondering if he'd deemed this situation unsalvageable.  Had he deemed this a loss?



Was there another maneuver he had in mind?  A bomb, a parahuman underling that he could sic on me?



Or would he seek leverage elsewhere?



\emph{My dad}.  \emph{The others.}



I suddenly felt the urge to get away, and get away \emph{quickly}.



My bugs hefted the items they'd successfully scavenged from pockets and pouches, carrying them to me.  As the soldiers moved to cover the weak points in the perimeter, I struggled to my feet and walked through the smoke to the point where two of the temporary fences joined together.  I used the keys my bugs had found and tried them, attempting to find the right key for the lock that linked the chain.



There were only so many possible keys, especially when I narrowed down the options to the three from soldiers nearest this lock.  It popped open on the second try, I removed the chain as quietly as I could, and then I bit my lip to keep from crying out as I shifted the two sections of fence far enough apart that I could slide through.



My bugs carried the fuming smoke canister a short distance ahead of me, giving me some added cover to slip through the point where the enemy lines were thinnest.



Their radios crackled with instructions from their captains, and the soldiers started tossing their canisters of smoke towards the house before they could be used against them.  It didn't matter.  I'd already slipped past the worst of them.  I approached one of the trucks that was furthest from the conflict.  My bugs were on the soldier's helmets, and I knew which direction they were facing, allowing me to stay behind them, using the soft soles of my costume to move in near silence.



``\emph{Behind you},'' my bugs whispered.  The soldier ignored them as he'd ignored the taunts and threats that were echoing through the neighborhood, without cease.



I slipped behind him and pulled his helmet off.  He drew in a breath to cry out an alarm and only choked on the flood of flying insects that flowed into his nostrils and mouth.  I was already dropping the helmet, switching my baton from my injured left arm to my right hand and striking the handgun out of his hand.  I had to strike him in the head five times before he collapsed, blind, gagging and choking on the bugs.



Maybe he was faking, maybe he was unconscious.  It didn't matter.  My bugs swept over him and checked every pouch and pocket.  I found his keys, then hurried over to the nearest truck.



I found the right key and started up the truck.



I'd turned sixteen without realizing it, not long ago.  It was fitting that I'd be teaching myself how to drive right about now.



Driving slowly so I wouldn't call too much attention to the fact that I barely knew what I was doing, I pulled away from the scene.



\sectionbreak



I pulled over, pulled the emergency brake because I wasn't sure how to park, then checked my satellite phone.  No service.  It made sense Coil would cut my lines of communication.  I tossed it out the window.  No use giving him a way to track me.



We'd moved towards the beach from Coil's place.  It made sense the other Undersiders would be heading north, to their individual lairs.



I was struck by an ugly connection between two thoughts.  Calvert had mentioned he had other matters to attend to, and if Chariot's teleportation device mimicked Trickster's power, they'd had to swap something or somebody \emph{in}.  If he'd replaced me with a body double, he would want to stay in contact with her and help ensure things went her way with the other Undersiders.



On the other hand, if Calvert was looking for a way to get leverage over me, my dad was one very vulnerable target that he was aware of.



I was left to decide if I would go check on my dad or tackle the bigger, cape-related issues.  It was a decision I'd had to make too many times in recent weeks.



It would have to be the Undersiders and Dinah.  I hated to admit it, but if my dad was attacked and I had the Undersiders there by my side, they could only help.  If the opposite were true, my dad would hamper me.



I disengaged the emergency brake and eased the truck into motion, fighting the urge to cough, knowing it would lead to wracking fits that forced me to stop in the middle of the street.



I'd seen how involved Calvert's maneuver had been at the debate.  He had a grand plan, and it wasn't necessarily the one he'd shared with us earlier.  I was now a glitch in his system, threatening to unravel everything he'd put together.



He had no reason to hold back, and he knew more about me than anyone I'd fought yet.  He'd tried to strike at me directly, and I'd only barely escaped.  I had little doubt he had other plans in mind, failsafes, traps and safeguards, and I had little choice but to run headlong into the thick of them.





