





Finding my teammates wasn't hard; Calvert was telling me where they were.



He didn't tell me \emph{directly}.  No, this was more a casualty of being too careful, of putting too many secondary measures in place.  He'd stationed soldiers to serve as lookouts at a wide perimeter around the Undersiders.  I noticed one group, turned the truck to drive around them, and then noticed the second and third.  They were three blocks away from the Undersiders, effectively surrounding my team, staggering their movements so only half were changing position at a given time.



I wondered how much battlefield experience Calvert actually had, or if it had been too long ago to matter.  Had he forgotten what it was like to actually be in pursuit of a target in the midst of a sprawling urban environment?  He probably could have tripped me up a fair bit more by dropping the perimeter and leaving me to try to track down my teammates.



No less than three radios for one squad buzzed with the noise of voices.  The three soldiers picked up their radios and replied.  Ok, so he was checking in with each squad.  So maybe it was roughly \emph{as} inconvenient as trying to find my teammates in the middle of nowhere.



Calvert had dropped me in \emph{Genesis' } territory.  It was about as far away as I could be from where I \emph{wanted} to be, about ten minutes drive down Lord street and then a ways towards the water, if someone was driving quickly.  I wasn't driving quickly; I spent far too long in the wrong gear, for one thing, I was clumsy with the car's controls and I was forced to drive even slower because the roads were treacherous.  Damage to the road was hidden in the areas that were still flooded, where my bugs couldn't necessarily see them.   Other roads were slick where there was \emph{just} enough water to raise the oils up from the crevices of the road's surface to the point that tires would slip on them.



On the plus side, driving while blind wasn't as hard as I'd thought it would be.  I was relying on my swarm, of course, but even then I figured the lack of sight would be more of an impairment.



After noting where the squads were deployed and coming to the conclusion that Calvert was using his soldiers to track the movements of my team, I had to stop to contemplate the situation and finally got around to the coughing that had been looming for a few minutes.



If I charged in, Calvert's men would collapse in on me.  Three or four soldiers per squad, and there had to be eight or more squads, unless Calvert wasn't keeping troops moving in advance of the group.  That made for twenty-five to fifty soldiers.  That would be pretty much all of Calvert's troops that hadn't been at the house.  I didn't fail to note how they were equipped, either.  I could sense the general shape of what would be sniper rifles and one piece of artillery that looked to be a mortar.



Made sense that he would have had the perimeter in place to ensure Dinah didn't slip his grasp.  If she was gone, then he might have maintained their positions to keep me from reuniting with my team after I escaped from his deathtrap.



Thing was, I had another problem here.  Calvert had teleported me.  I wasn't sure how he'd locked on to me, had ditched my phone as the most obvious measure, but I was worried that they could tag me with the thing and toss me into some backup trap reserved for one of my teammates.



All in all, I didn't want to give the soldiers a chance to see me, radio in general coordinates and then toss me out to some remote area on the other end of the city.  Knowing that his power was least effective when he didn't have a full grasp on what was happening moment to moment was another reason to keep out of sight.



I \emph{did} want to go on the offensive.  I just wasn't sure how.  If I attacked the individual squads, a check-in on Calvert's part would reveal that someone was picking them off and they would all go on the offensive.  They might even shoot to eliminate my teammates.  Grue, Imp, Bitch and the dogs might have the suits or natural durability to keep them alive in the face of a hail of gunfire, but Dinah didn't, and there was the possibility that the shots from the sniper rifles could penetrate the suits.



Or Calvert would order his squads to fire their mortars and wipe my teammates off the map.  If I assumed he had more than one mortar positioned around them, added his power into the equation to give him two sets of barrages with different target zones, I doubted they would emerge unscathed.



That left me to wonder why he hadn't done something similar at the house.  No grenades, no mortar, no bomb laying in wait.



Failing that, what was the trick behind the teleportation?  Why hadn't he just teleported me back after I slipped away?



Did he want to keep me alive?  Or had he actually expected me to escape?  Had he looked at all my past confrontations and gauged that I could probably make it, and it was no skin off his nose if I didn't?



Hell, it was possible he'd used his power to help ensure I'd make it this far, to further some greater scheme.



Whether I wanted to deal with the soldiers, get the Undersiders out of the way of those mortars or avoid falling into some greater trap laid by Calvert, I needed more \emph{information}.



The Undersiders were walking, judging solely by the speed the soldiers were adjusting their positions.  I wasn't sure where Atlas was, but I'd driven past the site where we'd picked up Dinah and he hadn't been there.  I could guess that Dinah wasn't keen on riding the dogs, so that made sense.



I slipped bugs into position on the soldiers to track their movements, then moved in closer, pulling the car into park and climbing out.  Better to move on foot.  I'd picked up masses of bugs on my slow-ish drive through the city, and I guided them as close to the soldiers as I could get them without giving myself away.



The tint of my lenses didn't help with the haze over my vision.  Still, opening my eyes, I could see it was evening, and the city wasn't offering much in the way of ambient light, given the inconsistent availability of power.  I coupled the use of my bugs with my eyesight to try to spot the glare of flashlights or headlights, but peeks suggested that the soldiers were operating in darkness.  Night vision goggles, perhaps.



I waited until the squad nearest to me shifted to follow, noted how the squads to the north and the southeast of them were holding position, guns at the ready.  Calvert would have told them I'd escaped and that they should keep an eye out.  Their wariness made sense.



Still, I was able to advance closer, following the group that was moving to follow, getting closer while keeping buildings and other obstructions between us.  Not the easiest thing in the world when I had to use the presence of the bugs to estimate where their line of sight extended, but I managed to get within half a block of them, crouching behind a van.  Swarms waited just around the corners.



I wasn't attacking, though.  No, my interest was on getting close enough that I could reach my teammates with my power.  Calvert had apparently stationed his men with my power's range in mind, but he didn't necessarily know that my power's range extended in certain circumstances.  Getting just a little closer, I could sense them, walking down the middle of the road.  I drew my bugs around me, not in the shape of a person, but to mimic the curves and bumps of the truck I was kneeling beside, so my silhouette wouldn't stand out so dramatically.



I could sense Bitch, still on Bentley's back as he trailed behind the rest of the group.  Bastard was lying across her lap, apparently asleep.



I sensed Grue and Imp, walking just ahead of Bitch and Bentley.



And I sensed Dinah, walking hand in hand with a girl who shared my build, who had hair of the same length and a costume similar to my own.  I didn't want to give anything away by swarming her with bugs to sense where our costumes differed, but it was pretty damn close.  She even had bugs on her costume.  Some were drawn there by pheromones, and some were pinned in place.  Her utility compartment differed from mine.  She had a knife, longer and narrower than mine, and two guns holstered within.  Some grenade canisters were tucked into the spaces by the shoulders where the short cape could cover them.



If Calvert's preparation of the building prior to teleporting me in hadn't made me think his betrayal was premeditated, this certainly cinched it.  Copying my costume, finding someone who fit my shape to the point that the others wouldn't notice?  Someone apparently capable of using a gun?



Dinah was still with them.  They hadn't dropped her off, even though Calvert could have arranged something like fake parents to accept Dinah.  Or maybe someone had raised that possibility and fake Skitter was taking Dinah back to `her' territory to look after for a bit. The other Undersiders would leave, maybe, and Dinah would go straight back to Calvert's possession.



I wished I had a better sense of Calvert's overarching plan.  What would happen to the other Undersiders?  What would he do with fake Skitter?  He couldn't hope to maintain the ruse for any meaningful length of time.



There had to be a reason he hadn't just bombed them here and erased the last of his enemies in one fell swoop.  How much of the plan that he'd shared had been real?



This situation wasn't so different from the one I'd just escaped.  There was the immediate threat, the mortars, and there was the one beyond that, with the soldiers ready to gun down my allies.  Bitch could have rescued Dinah, Imp and Grue from the mortars, given a chance to run, and Grue and Imp could deal with the guns, but the biggest issue, the biggest \emph{difference} in where they were now compared to where I'd been, was that they weren't aware of the threat.



If I could communicate with them, perhaps I could have coordinated them, managed something.  But it was evening and the black and brown bodies of my bugs wouldn't be able to spell out anything obvious against a dark background.  My phone had been locked out and the presence of the false Skitter meant I couldn't deliver a message unless it was very subtle.



Any mistake on my part threatened to provoke an ugly situation.  Calvert could order the mortar strike and teleport Dinah and false Skitter out.



No, I didn't think there were many options when it came to communicating with Grue.  Imp?  Maybe that was a better option, given her ability to disappear, meet up with me and then rejoin the others.



Except I didn't have an explicit strategy in mind, and I wasn't willing to gamble that Calvert hadn't accounted for Imp with some kind of surveillance with an electronic filter, like the screen of Dragon's battlesuit.



Rachel?  No.  I was pretty sure she couldn't read and write well enough to follow any directions, so I couldn't even explain anything complex without saying it aloud, and doing \emph{that} would be hard, speaking through my bugs without alerting the doppleganger in their ranks.



I could abandon them, try to find Tattletale or my dad, but Tattletale was going to be behind even more layers of security, if she was inside Coil's underground base, and going to see my dad felt like a detour that wouldn't do anything to address this situation.



That left me one potential ally.  I sent a ladybug to Dinah, settled it on her right hand, the one that the mock Skitter wasn't holding.



She glanced at it, her head turning a fraction, then moved her hand to hide it from false Skitter.  I felt her clench her fist, the skin between the ladybug's legs stretching so the legs were pulled slightly apart.



Dinah knew that Skitter wasn't me.  There was no other reason to hide the ladybug.



We'd never spoken.  We'd never had a conversation, or even communicated through more than eye contact.  Dinah had been driving my actions for weeks, now, or maybe it would be fairer to say my goal of saving her had been driving my actions.  Now we were finally getting a chance to interact, and everything hinged on it.



The bug crawled to the center of her palm, and she closed her fingers gently around it.  Did Dinah have access to her power?  Could she signal me?  Dropping the bug?  Killing it?



I sensed the movement of the bug as she raised it to her chest, used her thumbnail to scratch at her collarbone.



Maybe I'd pinned too many hopes on the drug-addicted preteen.



Maybe I'd read the little signals wrong, and she didn't realize that the Skitter next to her wasn't me.



Or maybe that niggling doubt that had been in the back of my mind since I'd decided I had to help Dinah had been real.  It was all too possible she didn't want to be rescued.  She was dependent on the drugs, she \emph{craved} them, and staying with Calvert meant she got them.  In a way, I felt like that possibility was why I'd been pushing myself to save her as hard as I had, because I suspected that Dinah was trapped in more than one way.  She'd been kidnapped, kept captive physically, but she was also being kept captive in other ways.  I \emph{had} to save her because she might not want to save herself.



Except if she didn't want to save herself, then \emph{this }situation would be that much more difficult to manage.



She dropped her hand to her side, let it swing a distance away, then brought it up to her chest again, scratched.



My doppleganger noticed, said something along the lines of `Don't scratch'.  I caught only some sounds, was left to put the rest of it together through cadence and context.  And, I thought, maybe it was easier to understand because she sounded \emph{familiar.  }She sounded much the same to the ambient bugs as I did.



It bordered on creepy.



The second thing I noticed was that what Dinah was doing was probably a signal.  Both times, she'd touched the bug to her chest, bringing it close to her heart.



Bringing the bug to \emph{her}?



I didn't like the idea of that.  If I was interpreting it the way I was supposed to, it seemed suicidal.  Did she want \emph{me }to come to where she was?  If she was, was her power guiding that request, or was she still powerless and simply wanting to be rescued?



Breaking past enemy lines without getting seen, only to\ldots what?  Make myself a mortar target alongside my teammates?  Where was the advantage?  What was the \emph{asset} to putting myself in the thick of it?



Calvert had to anticipate that I'd try to rescue my teammates.  His soldiers wouldn't be on guard against an outside threat like this if he didn't.  What did he expect \emph{I} would do?  I wouldn't charge headlong into his soldiers.  I \emph{would} see them.  I'd find some way around them, maybe turn some aspect of the situation to my advantage.



There were too many possibilities when it came to ways I might leverage things.  He couldn't narrow down what I'd do because that was how I operated.  I was versatile.



Then what was the common element?  I was tired, I was hurting, fighting the urge to cough, lest I inform the soldiers I was here.  I couldn't think of any solid way to tackle this situation, but in scenarios where I could, what might the common elements be?



I'd be using my power, for one thing.  Calvert couldn't do anything about that unless he'd had Leet devise some kind of counter-weapon.  It was all too possible, but I didn't have the time to consider all the possibilities there.



I didn't have the \emph{time}.



The other common element, the drawback to my power, to my mode of operation, was that I wasn't dynamic.  I wasn't a blitz hitter, in and out in a flash.  I could be aggressive, impulsive, improvising on the fly, but it took me \emph{time} to get my soldiers in a row, to prepare my tools and drag things to where I needed to be.  Fighting Mannequin had been like that, those two long minutes of sustaining a beating while I got all the supplies and spiders to the site of our skirmish.  Even escaping the house, it hadn't been quick.  I'd had to hunker down and amass enough decoys before dropping from the window.



Calvert had studied us.  He'd be aware of this.



Dinah and faux Skitter were walking.  Whatever excuse they'd given for not being able to ride Atlas, they'd opted to travel on foot instead of riding on Bentley or catching a ride in the truck Calvert's man had driven.  Maybe that wasn't because Dinah was scared of the dogs.  Maybe faux Skitter had suggested it, encouraged this for some greater plan.



They wanted to let me catch up.  They were betting I'd get here, then take time to deal with the squads so my teammates weren't in danger.  By doing that\ldots what?  How would he capitalize on it?



Identify the direction I was attacking from, then bring all the soldiers he'd had at the deathtrap house here to corner me?  Bring the Travelers?  \"{U}ber?  Leet?



Dinah struck the side of her leg with the bug she held, hard.  Grue said something I didn't catch.



The message was clear.  \emph{No}\emph{w}.  If Calvert was expecting me to delay, to take my time and be methodical about this, and Dinah was urging me to be aggressive, throw myself headlong into this situation, that had to point to something.  I'd decide what the hell I was supposed to do while I was en route.  I broke into a run.



I couldn't move directly to their location.  I had to backtrack, find a route that didn't put me in view of any of the watching squads.  The activity was making me cough, and I was forced to suppress it or limit it to muffled choking as I got closer to the soldiers.



Sweeping the whole of my range with my bugs, I found a route.  I had to backtrack a touch, move a bit closer to the water, but I found the construction site, and I found the ladder leading into a hole in the ground.  From there, it was a short climb to accessing the storm drains.



The acoustics of the storm drains made for a lot of noise, even if it wasn't raining aboveground.  The water varied from knee-high to waist-high, depending on how much debris had filtered down, and it was moving with enough speed that it interfered with my ability to run.  My chest screamed at me in pain every time I was forced to stoop down to touch ground with my good hand for added support, and I didn't dare cough for fear that the same acoustics that made the area echo with the flowing water would carry something to the ears of soldiers above.



The realization hit me when my swarm reached far enough to sense the second mortar and accompanying squad of soldiers.  There \emph{was} an advantage to putting myself in the middle of the mortar's target area.  I just had to get there.



I picked up my pace, hurrying in the direction of my teammates and Dinah, slipping on the slimy footing and loose grit, trying not to cough and failing.  It didn't matter too much.  I was past the perimeter and closing in on my teammates, using my bugs to figure out which turns I needed to make and which paths were most open to travel.



In a matter of minutes, I was close enough that I had to find a way up.  My bugs identified a ladder, and I pushed my way up, using one shoulder and my legs to lift the drain cover from its housing.



I emerged just far enough away that I thought the sound of the cover wouldn't be audible.  Bentley perked his ears up as I used my good hand to set the drain down, but didn't do anything further.



My concern and my worry were driving my range outward.  I was sending any bug I didn't need for sensing my surroundings to the periphery of my range, gathering them near the mortars.  Spiders threaded cords of silk together, and other bugs gathered en-masse.  Being here, at the bullseye, with my range extended like it was?  It meant I could strike at each of the four mortars simultaneously.



I hit each squad of soldiers in the same moment, a tide of bugs washing over them.  I tried to wind cords around the noses of the mortars, snag them on anyone who was moving, but they were too stable.



One soldier grabbed a bomb and moved to load it into the tube of the mortar.  In an instant, I had the full mass of that one swarm on him, slipping beneath the stylized, high quality armor and masks Coil outfitted his mercenaries with.  They bit, stung and attempted to wind cords around him, tying his hands, for lack of a better word.  He put the mortar down and backed off, and I eased up on him, settling for a more general form of attack.



Snipers couldn't fire, mortars were out of commission, and the soldiers weren't in a position to attack.



And faux Skitter raised her head a fraction, her back straightening.  If I could see, and if I were in a position to see \emph{her}, I might have missed it, but I was aware with my bugs on her. She knew.  A headset beneath her mask?  A communications device in her ear, feeding her info?



I ran towards my team.  Bugs stirred around the others, as I attempted to rouse them and get their attention.



Fake Skitter wheeled around, reaching behind her back to draw her gun.  Her arm caught Dinah around the shoulders, hugging the girl to her side.



I missed the first part of what she said.  The meaning was clear.  ``\ldots{}got no more use for you.''



And she sounded like me as she said it.  I could sense the shock on the part of my teammates.



And I could sense the trap fall into place, as though a switch had been flicked.



The bugs I'd placed on my teammates to sense where they were went on the attack.  It wasn't my command.



I tried to push the bugs to stop, but my power was drowned out.  It wasn't that the commands they were receiving were more powerful than mine, more that they kept coming, a singular, crude set of commands extending \emph{across }my entire range, maybe even further, every half second, overriding any ongoing instructions to my bugs.  \emph{Attack, move this way, attack, move this way}.



Grue said something, and I couldn't catch it.



``\emph{Betraying} us!?'' Bitch screamed the words.  Next to Bentley, she was suffering the worst of it as the bugs attacked.



``Sorry\ldots'' my doppleganger said.  I missed the tail end of what she said after that, but it ended with, ``\ldots{}the plan.''



\emph{Sorry, Bitch.  It was always the plan}.



``No!''  I shouted, and the act of shouting made me cough until my knees buckled.  I could feel the bugs gathering on me, attacking mindlessly, collecting on my scalp.  Still coughing, I reversed the short cape that sat around my shoulders and pulled it over my head to serve as a hood.  It didn't do anything to kill the bugs that were still alive and present, but it kept more from accumulating.



I was too far away for any of them to hear.  A block away.  Miles away, for all the good it did.



The other Skitter fired her gun at Bitch, one shot after another.  Grue blanketed the area in darkness, and the false Skitter dropped her weapon.  I could sense Bitch slumping on Bentley's back, Bastard spilling from her lap to hit the ground and roll on impact.



\emph{Did he clone me?}



No.  I could sense the movements of the bugs throughout my range, even if I couldn't control them.  They were moving in a massive, slow spiral, drifting counterclockwise and attacking anyone they came in contact with, and the center of the effect, where they were settling and gathering in piles?  A box in the center of one building.



Had to get there, shut it down.



I struggled to my feet, half-running, half-staggering as bugs gathered in a heavy carpet on me.  I was lightheaded, exhausted, still coughing, and the first of the bugs were arriving from where they'd been attacking the soldiers.



I sensed Dinah in the midst of the swarm.  The pheromones that false Skitter wore were serving to override the pulses from the box, keeping bees and wasps from doing too much damage to the pair.  I wasn't sure how they planned to deal with the more dangerous spiders, but the bugs that were moving across land were slowed by the constant vertical ascents and descents as they ran into buildings and other features of the landscape.



False Skitter hurled a canister into the midst of my teammates.



A flashbang.  I could see the flare of light, the concussive sound that scattered the bugs that had congregated on them.  Heading for the swarm box, I wasn't close enough for it to really affect me.



The mortar crews were packing up their equipment and climbing into the trucks to beat a retreat from the scene.  \emph{This is Calvert's doing}.  He was convincing the others that `I' was turning on them the second I had Dinah.  He'd probably rigged it so I would disappear afterward.  Skitter out of the picture, in a way that was totally believable given my prior actions.  The Undersiders would be mad, they'd be hurt, but they'd still be \emph{his}.



Except I was here.  I could convince them it was a trick.  Either shut off the swarm box or take a left turn, show up where they were, and things would make sense in an instant, two Skitters, one a fake\ldots



No, I had to shut off the box.  I could feel blood, where some bugs had found flesh on Rachel and the dogs.  If too many bee or wasp stings struck home, someone could be seriously hurt, needing epinephrine.



I could sense Dinah moving one hand, drawing it across her chest in deliberate gestures.  From shoulder to shoulder, down the side of her body from her armpit, turning to cross the base of her ribs\ldots



\emph{Letters}.  S.  O.  R.  R.



There was no time for the Y.  Both Dinah and the other Skitter disappeared, replaced by a collection of rubble and a single flashbang.  The others were still reeling from the first when the second flashbang detonated.



More boarded up windows and doors.  I fired my gun at the handle of the door and then kicked.  I did more damage to myself than the door, collapsing in another coughing fit.



The others recovered before I did.  I could sense Grue standing, shouting something.  I couldn't understand him with the effect his power had on his voice.  Not the first time I'd run into that issue.  Rachel was up too, using Bentley to stand, one hand pressed to her side.  I sensed the hot knot of metal where it had impacted the reinforced jacket I'd given her.  Good.



``Find her!'' she shouted.  ``Find Skitter!  \emph{Hurt}!  \emph{Kill}!''



Bentley broke into a run, zig-zagging across the street they were standing on toward where false Skitter had been.



\emph{Did they make her }\emph{smell like me?}  They had to have, to keep the dogs from barking distress.  But how?  Had Calvert had his men raid my stuff?  Had he used my dirty laundry?



I felt \emph{violated}, not just because of the potential trespass, but the extent to which they'd stolen my identity and abused it.



Bentley raised his head and then turned right in a loping run that would put him behind me in a matter of seconds.  Then he'd have my trail, he'd zone in on me\ldots I could picture what happened next.  I wasn't in a state to put up a fight.



I climbed to my feet, reloading my gun, then fired three more times at the door handle.  A gnat that was following the spiral summons of the swarm box made contact with a deadbolt on the far side of the door, and I shot at that too.  This time, when I kicked, it opened.  I collapsed to the ground, my cough so fierce and ragged that I wouldn't have been surprised if I'd been expelling flecks of blood into the inside of my mask.



Bentley spotted me and began charging.  I crawled inside, brought my legs up to my chest to get them out of the way of the door, and kicked it shut.



The mutant bulldog was too large for the door.  When he impacted it, it split across the midsection, the upper half coming free of the hinges, and the surrounding brickwork bulged inward, cracked mortar showering down around me.  The wooden framework around the door kept him from getting much further, wooden pillars of support that were a foot thick on each side.  It made sense that Calvert had picked a fortified structure to stick the  swarm box inside.  Small blessing that it afforded me some small advantage as well.



Bentley butted his head against the doorway again, getting no further than before, then backed away a few steps and howled.  Bitch and Grue were already en route, following the sound of gunshots.  I could hear Bitch howl a response to Bentley's cry, an utterance of raw anger and promised violence.  Bastard was at Bitch's side.  He was bigger, growing spikes of bone and an armor of calcified muscle.  \emph{He} would fit through the door.



I crawled for the swarm box.  The bugs were thick, and though they couldn't penetrate my costume, they were making their way into the folds at my neck, around my hood.  It was due to numbers rather than any design, but it was stifling.  I could barely breathe, and having to climb through a mass of bugs as big as a large tank, feeling them biting, stinging, feeling the venom the wasps and bees were injecting into me\ldots



I raised myself up enough to get a grip on the tarp that covered the box, and then let myself collapse to the ground, coughing, maintaining my grip so I pulled the tarp off as I fell.  I was seeing bright spots in my vision, which shouldn't have been the case, because I couldn't see anything.



Getting onto my knees so I could find the wires of the swarm box was a gradual process, made heavier by the mass of bugs on and around me.  Every bug for what had to be at least a mile in every direction, gathering here.



I tore at one handful of wires.  Nothing.  It was just a matter of time.  I had a minute or two, judging by the speed Bitch and Grue were moving.



I reached to grab another and felt a hand on my wrist.  Imp hauled my hand back, pulling me off-balance, then kicked me square in the chest.  I doubted there was a place she could have hit me where it would have hurt more.



I lay on the floor, alternately writhing and spasming as pain lanced through me.



``Did the doggie get you?'' Imp growled the question.  ``\emph{Good}.  Turn off your \emph{fucking} power.''



I had only a helpless noise to offer in response.



``I warned you.  Warned you what you were in for if you let my brother down.  So do I use the knife, make it quick?'' she drew a knife.  Then she drew her taser with her other hand, ``Or do I stick you with this until you stop using your power?  Then we can find some place where you don't have your bugs, and take the \emph{slow} option.''



Grue and Bitch entered through the door, and I heard Grue mutter something.  Bitch gripped Bastard by the collar.



``Imp.  You found her,'' he said.  He sounded strangely unaffected by recent events.  There was no emotion to his voice.



``We were just discussing options.''



``I heard.  Taser won't do anything.  Worse than anything, she'll use her power while she's asleep,'' Grue said.



I opened my mouth to speak, coughed instead.



``What about if she's dead?'' Bitch asked.  She \emph{didn't} sound disaffected.  She sounded pissed.  ``I can do it, if you two can't stomach it.''



The lack of a response from Grue was unnerving.  He kneeled beside me, putting one knee on my bad wrist.  I cried out in pain, coughed more.  He just stared.  Not that he could see much, with the way the bugs filled the room.



When he finally spoke, it was one word.  ``\emph{Why}?''



I struggled to gain my breath, to center my thoughts.  I felt dizzy.



What could I say?  Was there anything that would convince them?  If I said it wasn't me, would they believe me?  If I turned their attention to the swarm box, would they think it was a bomb?



He waited patiently for me to recover enough to respond.



``Use\ldots'' I wheezed in a breath, ``Dark.''



I closed my eyes as the darkness flowed over me.  I felt my power weaken, realized I'd unconsciously been pushing the bugs to hold back.  I felt their attack intensify.



Grue stood.  He opened his hand, fingers splayed, and his darkness dissipated.  He turned to Bitch, gestured to Bastard.



``Yeah?'' she asked.



``Yeah.''  He pointed.



``You sure?''



``I'm sure.''



Bitch whistled, Bastard lunged, and the swarm box caved in beneath the wolf cub's front paws.



The swarm went quiet.



Grue offered me a hand, I took it, and he hauled me to my feet.  I was unable to balance, dizzy, and leaned heavily into him.



``You're not buying this, are you?'' Imp asked.



``It wasn't her.''



``She's playing you.''



``\emph{It wasn't her}.''



Imp folded her arms.  Bitch didn't move.



Grue murmured, ``Explain what's happened.  Then we need to take care of you.''



I shook my head.



``No?''



I coughed briefly.  ``Tattletale.  Regent too.  They're in trouble.  We left them with Calvert.  With Coil.''





