





With Grue's help, I seated myself on the intact edge of the destroyed swarmbox, scattering my insects to the walls and ceiling of the room.  Grue paced a little, while I eyed Imp and Bitch.  My female teammates didn't look entirely convinced, and I couldn't blame them.  They'd just seen someone who matched my description attacking them.  The nighttime darkness and the lack of city lights hadn't helped, and the obscuring swarm of bugs had helped hide the details from the moment the impostor gave them reason to suspect her.



``What happened?'' Grue asked me.



``We arrived at the place he was keeping Dinah, she grabbed my hand, we turned around, and the headlights flashed.  Then I was somewhere else.''



``He switched to his highbeams, momentarily.  Don't know about the others, but my eyes had adjusted to the dark.  I couldn't see anything, used my darkness to try to cover us in case he was pulling something, but nothing happened.  Turned around and you were fine.''



``Except it wasn't me.''



Grue nodded slowly.  ``Looked like you, sounded like you.''



``I don't know how.  Genesis?''



``Didn't strike me as much of an actor.''



``Then I don't know,'' I said, feeling lame.  I knew I didn't sound convincing.



``What happened?  Was he only trying to separate you from us?''



``I'm ninety-five percent sure he tried to kill me.''



``What's the other five percent?''  Grue asked.



``I'm not a hundred percent sure of \emph{anything}.  But he didn't have a bomb waiting to go off when I arrived, so that leaves me with some doubt.  He \emph{did} shoot me, and set the building on fire around me.  And he had soldiers waiting to gun me down if I stepped outside.''



``Did he want you to come here, to frame you?''



``No,'' I said, shaking my head.  ``Doesn't make sense.  Just as easy for `Skitter' to disappear with Dinah, leaving you guys angry but still loyal.  I think the way he wanted it, I'd die of the gunshot or burn up in a housefire, and he could use the lack of living reporters in Brockton Bay alongside some bribe money for the Travelers to ensure you guys didn't know what he'd pulled.  Maybe something comes out later about me betraying you, to put it in perspective and put any lingering doubts to rest.''



``He teleported you into a burning house, shot you, surrounded you with soldiers.  And you escaped,'' Imp said.



``Barely.''  I touched the knot of metal where the bullet had settled in my armor.  ``I guess it's bulletproof after all.  I got away because of stuff he wasn't aware of, mainly.  My costume, tactics I've been using in the field, the fact I had a gun.  Don't know if Calvert knew about that.  Are you okay, Rachel?''



Rachel didn't respond.  Her head was turned my way, and I could imagine her staring, trying to read me.  Her hand gripped the chain at Bastard's neck.



``It wasn't me,'' I told her.



``It wasn't her,'' Grue confirmed.  ``I saw with her power.  That box was controlling the bugs.''



Bitch nodded slowly.  I couldn't see her expression to know whether she was glaring at me or narrowing her eyes behind her mask.



``If you have any doubts,'' I said, ``You can stay in a position to attack me if something happens.  One whistle or one hand signal away from commanding Bastard or Bentley to tear me apart.  I hope you won't leap to any conclusions, but-''



``It's fine.''



``Are you sure?  Because I don't want there to be any hard feelings or\ldots I don't want there to be hard feelings.''  I'd almost said retaliation, but I'd decided I didn't want to bring that up.



``It's \emph{fine},'' she said, and there was a touch of anger to the words.  ``This shadow and dagger shit pisses me off.''



``Cloak and dagger,'' Imp offered.



Bitch made a low, grunting noise in her throat that fell somewhere between a huff of anger, a belch and a grunt.  ``The way you acted before, the way that person acted when she shot me and the way you're acting now, none of it makes sense, and maybe that's 'cause I'm stupid.  But I'm going to handle this my way.  Next time someone shoots at me, I kill them.  Or I have Bastard eat their hands and feet.''



``You shouldn't maim people,'' I said.



``Says the person who just emptied a gun clip at us,'' Imp said.  When Grue and I turned her way, she raised her hands, ``Kidding.  I'm just kidding.''



``\ldotsWant me to kill them instead?''  Bitch asked.



``No!  No.  Just\ldots nevermind.  But hold back a bit for now.  And don't call yourself stupid.  You think in a different way, that's all.''



She offered a noncommittal grunt in response.



``We should talk rescue plans,'' I said.  ``Calvert invited Tattletale to join him, probably so she wouldn't tip us off about the body double.  That means she's probably caught.  Regent too, since we sent him to look after her.  This is the kind of situation we were hoping to avoid by playing along with his grand plan.''



``Having to tackle his full forces to save Tattletale, Regent and Dinah.''



``Right.  If we go charging into this, we or one of his hostages will get killed.''



``I could go in,'' Imp said.  ``Get them, walk them out.''



``No.  He knows us.  He's anticipated something like this.  Probably has for the Travelers, too.  He'll have planned around our powers, with counters in mind for each of us.  That means video cameras to keep an eye out for you.''



``Pain in the ass.''



``Indirect attack?''  Grue suggested.



``It won't work if he's holed up somewhere safe.  Not with the countermeasures he'll have put in place.  If he's in his underground base until this all blows over, then he'll be impossible to access,'' I said.  I had to stop to cough.



Nobody chimed in with an answer or idea while I recovered.



I went on.  ``If he's in the PRT offices, then we'll probably have to get past the Travelers, his soldiers, his \emph{PRT officers, }any countermeasures he's put in place and any countermeasures the \emph{PRT} put in place.  It'd be a question of staggering out his various lines of defense so the more questionable ones are out of sight of the good guys.''



``And he still has his hostages,'' Grue said.



``\emph{Fuck it},'' I groaned, then I coughed more.



``You need a hospital,'' Grue told me.



I shook my head, then regretted it.  I felt dizzy.  Vaguely nauseous.  It was as though simply stopping and letting the adrenaline kick down a notch was letting symptoms emerge.  ``Can't.  Not now.''



``You're nearly dead on your feet.''



``I'll manage,'' I said.  I turned my eyes to the place I'd been lying while Imp stood over me.  ``What if I \emph{was} dead?''



``Hm?''



``Calvert doesn't have a way to know how this turned out.  Do you have phone service?''



Grue reached for his phone, but Imp had hers out first.  ``Sure.''



``He cut my phone off.  I threw it away in case it could be used to track me, or in case it was how he was getting a hold on me with that teleportation device.  If he suspected you, wouldn't he do the same, limit your options?''



``So you think \emph{he} thinks maybe something happened.  Or he's waiting to see if we bought his ruse.''



``He knows I was in the area.  I attacked his men trying to save you guys.  He had gunmen and explosives teams ready to wipe you off the map if you caught on to what that impostor was doing.  So what happens if you call him and tell him you killed me?''



``He asks us to meet him at one of those secure locations you mentioned, and we can't refuse without revealing that we know what he tried to pull.  And destroying that box might have clued him in anyways.''



``Fuck,'' I muttered.



``When the other Skitter disappeared with the girl, how did she do it?  Exactly.''



``Teleporting,'' I said.  ``Threw the first flashbang, teleported out, leaving rubble and another flashbang behind.''



``Mm,'' he said, ``Okay.''



``Why are you so curious about that?''



``Just thinking something through.  Give me a second to think.''  He pointed at me, ``Make sure you're taking deep breaths in the meantime.  Even if it hurts.''



I nodded and did as he asked.  For a little while, I ignored my bugs and focused on tallying the damage I'd sustained.  My breath wheezed and rattled, my chest hurt every time it or something attached to it moved, and my eyes stung when I opened them.  Not that there was any point.



Grue was pacing, breathing hard, while Imp and Bitch stood by.  It was a bit of a reversal of the norm.  I could sense Bitch scratching around Bastard's ears, her fingernails digging in deep to get past the areas with armor and bony spikes.  Imp was on the other side of the room, leaning against one of the wooden pillars and watching her brother.



``I'm calling him,'' Grue announced, still panting a bit.  Before any of us could protest, he said, ``Quiet.''



I closed my mouth.



He put the phone on speaker.  I could hear it ring.



Funny how something so mundane as the ring of a phone could sound so ominous and eerie, given the context of a situation.



``Grue,'' It was Calvert's voice.  ``What-''



When Grue spoke, his words were growls, barks.  ``You better not have had anything to do with this, or I swear, this is over.  We're done, gone.''



I could virtually \emph{hear} Calvert switching mental gears to try to adapt to this.  ``Slow down and then explain.  I don't know what you're talking about.''



``Skitter attacked us and then she used \emph{your} technology to leave the scene.  I know you wanted to keep that girl, but going so far as to fucking turn on us-''



``Grue,'' Calvert's voice was hard, firm, ``\emph{Slow down}.  It doesn't make sense that I'd arrange things that way.  Why go through the motions of giving my pet to Skitter, only to\ldots you haven't fully explained what happened.  You said she \emph{attacked} you?  Are you sure?''



``Pretty \emph{fucking} sure, Coil.  She shot Rachel and then turned on me.  Imp disarmed her.  Then she teleported away using the same device \emph{you} described to us an hour ago.''



``I\ldots I see.  Is Rachel all right?  And who else was with you, my driver?  You're all unharmed?''



``Your driver went ahead.  No, we're all fine, except for Skitter.''



``You said she teleported away.''



``She didn't get more than two blocks away.  We chased her down and stopped her.''



My eyes widened a bit.  I could imagine Calvert's next words before he spoke them, was already moving.



``Show me.  Send a picture through the phone.''



I shifted position so I lay in the depression that Bastard's front paws had made in the swarm box.  It was a scene I had to stage in seconds, using dragonflies and wasps to carry hairs across my mask, moving my hand so my wrist bent at an awkward angle where the metal folded.  The final touch was bringing all the bugs from around the swarm box to carpet me and the floor.



Not a half second after I finished, I heard the digitized camera sound.



``I see.  That's quite unfortunate.  Where's Dinah?''



\emph{You know where Dinah is.}



``I don't know,'' Grue said.  ``I'm far more interested in hearing how Skitter managed to use \emph{your} technology to do this.''



``You're sure?''



``I saw it with my own two eyes,'' Grue said.  ``She threw a flashbang, but light and darkness don't affect me the way they do others.  You know that much.''



Grue was lying, adding an element Calvert wasn't aware of, to throw him off track.\emph{  Good.}



``I didn't, believe it or not,'' Calvert said.  ``And I don't know how she would have gotten access to the controls.  One moment.  I'll have to call you right back.''



My swarm felt Grue stiffen.  He raised his voice, ``Don't hang up on me!''



The speaker phone buzzed with the dial tone.



We stared at each other.  Or the others stared and I used my swarm sense to observe.  As a group, we were still and quiet for long seconds, the dial tone still blaring.



Grue hit the button.



``What are you doing?'' I asked.



``Being aggressive, keeping him on his heels.  If he's constantly defending himself, he won't be able to turn things back on us.''



``Except he hung up.  He's going to think through his options and give you an excuse when he's ready.''



``I didn't think he'd hang up.''



I frowned.  I was thinking back to the meeting I'd had with the school, when my dad had been with me and we'd accused the trio of bullying.  Both Emma's dad and the school had played their little power games.



``It's a tactic,'' I said.  ``He regains control of the situation by being the one who can call back, and it helps establish the idea of him being an authority figure.''



``Damn,'' he said.  ``Sorry.  It made sense in my head, but I didn't think it through, I'm tired.  Didn't sleep last night.  I figured it was better to call sooner than later.''



``It's okay.  Maybe call him back?''



He didn't get a chance.  The phone rang.



``This wasn't the kind of response I wanted, Coil,'' Grue growled into the phone, the second he'd answered.



I heard the beep as he switched it to speaker phone.  Calvert was already talking.  ``- have sequestered Regent in my custody, out of concern that he controlled Victor to have the young man hack into my systems.''



``You and I both know that Victor didn't have that kind of access, and we didn't know about your teleportation technology until an hour ago.''



``I fear \emph{Skitter} may have known, and I'm simply covering my bases.  Once we've verified what happened and that Regent wasn't complicit, I'll release him.  You can understand where I'm wanting to be careful, given this turn of events.''



``I don't understand anything, Coil,'' I heard a tremor of emotion in Grue's voice.  ``I \emph{liked} Skitter, and she's dead.  The use of the teleporter says you're complicit.  I want to look you in the eye and \emph{believe }you weren't a part of this.''



``We'll sort this matter out.  If you'll come to my headquarters, we can discuss this.''



``No.  Not your headquarters.  Not with the possibility you pulled this shit on us.  We'll meet somewhere else.  Somewhere open.''



There was a pause.  ``As you wish.  Name a location.''



Grue, this time, was the one caught off guard.  Calvert's response was fast, and Grue clearly didn't have an area in mind.



\emph{A place where we'd be able to set up faster than Calvert, ideally open, not riddled with attack routes and vantage points for his soldiers}\ldots



I thought of a spot, and the air caught in my throat as I suppressed a small noise.  I almost coughed.  I drew the word in the air with my bugs.



``The market, north end,'' Grue said, reading it.  ``You know it?''



``I do.  It's shut down at present.''



``Right.  You come with only one small squad of soldiers, bring Tattletale and Regent.''



``If-''  Calvert started.



Grue hung up on him.  He looked at me, ``Authority, right?''



``Right,'' I said.  But all I could hear was the emotion in his voice when he'd been talking about the \emph{idea} that I'd been dead.  Pretending.  Grue wasn't a guy who showed his emotions, he didn't strike me as an actor.  Hearing that had affected me more than I thought it would.  I didn't want to ask if it was because he really cared or if it was because he'd tapped into something else, some vulnerability that his recent trauma had left open to him.



I coughed lightly.  ``The market's a good spot.  His people were at the south end of town.  It'll take him a bit to get there, so he won't be able to stage any kind of ambush.''



``It works.  But if we're meeting him, what are you doing?''



``Staying nearby,'' I said.  ``I'll wait in the wings.  In the meantime, we should see if we can get our hands on something that we could have Bastard maul to the point that it looks like my mutilated remains.''



``There a butcher still in service anywhere?'' Grue asked.



``We'll figure something out,'' I replied.



\sectionbreak



The market was almost empty, an expanse of asphalt devoid of cars, surrounded by tall grass.  There were still faint marks where the treads and scoops of bulldozers had pushed the dirt and debris to the far side of the lot.  Only a few stalls were standing, but the displays were empty.



I felt exposed, naked.  I was wearing only my old costume and the built-in makeshift skirt to cover me where the fire had eaten away at the leggings.  My utility compartment was the one that had been damaged during our altercation with the Nine, holding the bare essentials, while my new mask and the upper half of my remade costume were presently being worn by the fake we'd made.  The sacrifice of the costume hurt, and the process of putting the fake together hadn't been pretty.



The head, upper body and arms were simply taken from a child's mannequin we'd salvaged from the inside of a store display and stuffed into the top of my costume.  To get the meat for the torn midsection, I'd had to use my bugs to root out and kill a raccoon from the bins of a dumpster.  I'd cut it open and tied the entrails to the base of the mannequin's torso with my spiders.  A wig that vaguely matched my own hair was simply bound to the head.  We soaked the body, the wig in particular, with the blood of the dead raccoon.



Bentley's tail wagged as he carried the thing delicately in his heavy jaws, one arm and a bloody mess of hair dangling from the left side of his mouth, raccoon intestines hanging out the other.



I headed into the tall grass and hunkered down.  Volumes of insects and arachnids that I'd picked up during our trek to the market settled around me, hidden at the base of the grass.



Adrenaline kept me awake, despite the fatigue that I was experiencing.  It had been an intense few days, an intense few \emph{weeks, }with minimal chance to rest.  My body was probably struggling to heal, and draining what little reserves I had remaining.  Still, I wasn't about to doze off.



Calvert arrived after ten or fifteen minutes, pulling up with one armored van.  All in all, he had only four soldiers with him.  He walked within twenty feet of me as he crossed the tall grass.  I was aware of his footsteps crushing my bugs as he passed over the swarm.



Oblivious, he approached Grue, Imp, Bitch and the dogs.



``Ah.  You brought Skitter.  It seems there's little doubt she's dead.  A terrible shame.''



``No kidding,'' Imp said.



``I'd suggest my man look over the body, verify that it was her, but I suppose there's no point trying.''



``Bentley wouldn't let you get that close to his treat,'' Bitch said.



Bentley growled, as if he understood the words and wanted to make it absolutely clear.



``Don't talk about her like that,'' Grue said.  ``Calling her a treat?''



``She betrayed us,'' Imp said.  ``Why do you care?''



``Enough,'' Calvert said, his voice hard.  ``Enough bickering.  My time is valuable, and I'm not willing to waste it on entertaining this ruse.''



I didn't have many bugs deployed on my allies or on Calvert, but I could still feel the others tense in surprise.



``Yes, I know.  I commend you for trying, I might have believed you, but I do have other resources on hand.''



``Then-'' Grue started.



``Ah, bup bup,'' Calvert raised a hand, ``I was talking.  As I was saying, I have other resources available.  I have a small cadre of supervillains, a small group of heroes, all the resources of the PRT and PRT computer systems, and all of their \emph{tools}.''



He snapped his fingers, and soldiers began to teleport down to the edges of the market.  Most were positioned so that the Undersiders would have to run off the edge of the pavement, over the grass and into the water if they wanted to get away.  Surrounding a target while holding guns only promised to get people shot.  The effect, as it was, was good enough.



The Travelers teleported in behind Calvert, followed by Chariot, Circus, \"{U}ber and Leet, and a few of his lieutenants.  People in suits.  One held a laptop while the other typed on it.



Every gun, tinker made or otherwise, was pointed at my teammates.



Another gun pressed against the back of my head.  Soldiers had teleported in behind me.



I felt despair sweep through me.  \emph{No}.\emph{  Too many.  Didn't think he could teleport this many in.}



The gun barrel prodded me, and I stood.  I walked with the gun pressed between my shoulderblades, just above the spot where my utility compartment hung.



``Skitter.  How nice of you to join us.''



``Cut the fake civility,'' I said.  ``Where are our teammates?''



``Regent and Tattletale are safe and locked up, rest assured.  I must say, I'm quite disappointed.  I really had hoped this would work out, and the loss of the Undersiders sets me back by weeks or months in the grand scheme of my plan.  Imp, you can cease trying to run.  My men have cameras on you,'' Calvert gestured toward the laptop.



Imp moved her mask to spit on the ground, just to my right.  It was a bit of a shock to find her standing there.



``Farewell, Under-``



``Wait.'' I said.  Raising my voice made me cough.



``I don't see any point to waiting.''



I hurried to recover and speak before he could give the order.  ``Dead man's switch.''



Calvert sighed.  ``Ah.  You are \emph{irritating}, you know?  On more than one occasion, I know, you've argued for the sake of the greater good.  I've viewed the recordings the PRT has of your appearances at major events and I've come to know you fairly well.  It's rather \emph{hypocritical} that you're now working so hard to fight \emph{against} the greater good.''



``Against your rule.''



``Essentially so.  If you simply would have died quietly, the Undersiders wouldn't have been stirred to rebellion, I could have established a peace we haven't seen since the day Scion arrived and everyone involved here could have walked away happier and healthier.  Your friends included.''



``Tattletale excepted,'' I responded.



``Tattletale excepted, I admit.  Too dangerous to be left unchecked.  A shame.  Now, you were saying?''



``I arranged a dead man's switch.  Kind of.  Unless one of my subordinates receives a message from me every twenty minutes, she'll mass-send emails to everyone important and even a few unimportant people.''



``Detailing the true nature of Thomas Calvert, I suspect?''



``Yeah.''



``I hate to break it to you, dear Skitter, but this isn't enough leverage for me to let you walk away.''



I turned my head in the direction of my teammates.  With my power, I noted their presence.  Grue, Imp, Bitch, her dog.



``None of us?'' I asked.



``No.  I'm more confident in my ability to handle the chaos that any email creates than I am in my ability to get you and your teammates under my thumb again.''



``Okay,'' I said.  I could feel sweat running cold down the back of my neck.  ``Then I have a few questions, and a couple of requests.  Satisfy that, and I can disable the dead man's switch.''



``The requests first, if you please.''



``Dinah goes free when you're done.  You don't keep her forever.''



``Agreed.''



``My dad, you don't touch him.''



``I haven't and I won't have reason to.''



``And you take care of Rachel's dogs.''



Calvert nodded, but I could sense his patience was running out.



``You do what you can to stop Jack from doing what he can to end the world.  If you have capes at your disposal, you give them some job related to that.  To stopping it.''



``Fine.  Is that it?''



``If none of us \emph{here} get to live, at least promise Tattletale gets to.''



``Fine.  That can be arranged.''



``I'll need to see her, to verify she's okay.  I get that you can't prove you haven't gone after my dad in retaliation for earlier, but you can bring \emph{her} here.''



Calvert nodded at Chariot, who pressed a button on his wrist.



Tattletale appeared in a flash of light, arms bound behind her, legs shackled.  She wore headgear that had her blindfolded and gagged.  I couldn't quite tell, but it looked like the ears were plugged too.



``Satisfied?'' Calvert asked.



``No.  It could be a body double, like you arranged for me.  I'd like to confirm with her.''



``No.  The restraints are in place for a reason.''



``Then it's a body double,'' I said.  ``And I'll let the timer run down on this damaging piece of email.''



``I'm willing to run that risk.''



``Use your power,'' I told him.  ``I'm going to say the words rose-L.  She'll reply with something green, followed by the letter A.''



``I'm familiar with your codes.''



``Great.  And if she doesn't, shoot us.  If there's a problem, go with your other world.''



``You know how my power works?'' Calvert sighed.  ``I suppose I shouldn't be surprised in the end, with the name she chose.  \emph{No}.''



``It's all I'm asking for.  You can send your computer experts to the destination I name, they'll check the computer memory to verify no messages were sent, check the phones of everyone on my call history that you don't already know, and then you'll know you're in the clear.  That's what I'm offering you in exchange for the assurance that at least Tattletale will get to live.  Peace of mind.''



``I could kill your liaison, you realize.  She's a loose end.''



I thought of Charlotte, hoped I wouldn't regret getting her involved.  ``I hope you won't.  All I've told her is that she should await my message and send the file I composed if she doesn't hear from me regularly.  I hope you'll let Tattletale and my civilian live, but if you won't, if you break your word, I guess I'll have to live with you looking a little worse in the eyes of the people who work for you.  Like the Travelers.''



``Don't bring us into this, Skitter,'' Trickster said.  ``This is your mess.  Your consequences.''



``I didn't \emph{do} anything.  He was the one who turned on us first,'' I protested.



I sensed Trickster turn Calvert's way.



Calvert sighed audibly.  ``As Skitter knows about my power and ever so kindly revealed the broad strokes of it to everyone in earshot, I suppose there's no loss in explaining.  I tortured one member of the Undersiders for information, in another world, days ago.  They revealed that you were plotting to turn on me if I refused to release Dinah.  I cannot afford to release her, so my hand was forced.''



``So it's \emph{our} fault?'' Imp asked.



``Ultimately, yes.''



``How did you make those body doubles?  Genesis?''



``The old-fashioned way.  The one that replaced you was a Sudanese child soldier.  I was preparing for the eventuality of your betrayal since the day after Leviathan attacked and your\ldots wobbly allegiances became perfectly clear.  It's amusing, but the files you stole from the PRT offices after rejoining the Undersiders supplied much of the video footage my hired experts used to coach her in the particulars of how you move and speak.  When you went to convince the Mayor of our way of thinking, Trickster carried the devices Leet designed to record the particular signals you use to command your bugs.''



``Which is how you built the swarm box.''



``The Famine Engine,'' Leet said.



``Whatever.''



``Any further questions?''



``Why didn't you drop me on top of a bomb?''



``An unfortunate side effect of Leet's power.  Leet believes it was the proximity to the bomb or the particular signature of the vat of acid that made it so likely to occur, but with my power I observed that it wasn't merely a \emph{chance} that the teleportation would fail and your well-trained body double would be caught instead, but a surety.  No less than twelve tries with the variables changed slightly.  Leet's power sabotages him, it seems.''



``Is that Leet's passenger at work?''



``Passenger?  Ah, that's what Bonesaw calls the agents.  Yes, I suppose that might be the case.  In any event, we nearly ran out of time before verifying that guns, fire and alcohol wouldn't skew his power.  Whatever the cause of the errors was.''



``Okay.  So I don't suppose you want to let me confirm it's Tattletale and tell you who to contact to cancel the dead man's switch?''



``No.''



``You've been careful every step of the way.  Thinking five steps ahead, amassing resources, amassing top-notch underlings, getting \emph{us} working for you, getting the Travelers.  I'm surprised you're willing to let things go ass-backwards when you're so close to tying up the last loose end.''



``It's precisely because I'm careful that I'm not willing to let Tattletale open her mouth and speak.''



``You're still pretending it's Tattletale,'' I said.



``It is.  I had no reason to arrange a body double for her as I did for you.''



``You had every reason.  Like you said, you didn't trust her, you couldn't let her work unchecked, and it would have been too unusual if the two members of the Undersiders that posed the biggest threat to your goals happened to disappear at once.''



Calvert shook his head and touched fingers to his forehead, as if exasperated.  ``Your underling and Tattletale can live.  That's all I'm willing to offer.  You'll have to take my word on both points''



``Your word is worth \emph{nothing},'' Bitch spat the words.



Calvert reacted as if he'd been slapped.



``You promised me safety, security, so long as I joined this team.  I've never been less safe, less secure.  Everybody lies through their teeth.  Maybe there's a couple of them I can stand anyways, but they're still liars, they've made me a liar, and you're the worst liar of them all.  It's fitting you wear a snake on your costume.''



``\emph{Enough},'' Calvert said, ``Anything more and I'll order my men to shoot you.''



``Shoot her and you'll never get the info you need from me,'' I said.



``You're a \emph{cheat}, Coil!'' Bitch barked.



``I'll have your \emph{dogs} shot if you say another word,'' Calvert said.



Bitch fell silent.



Silence reigned for long seconds.  I was aware of my bugs, knew that I couldn't have them attack without us getting shot.  I knew my armor was bulletproof, Bitch's armored jacket was the same way, but the thinner fabric, or a bullet through the lens or eyehole of a mask?  There were a lot of soldiers here.  Even if the suits could stop the bullets from penetrating, we could be pulverized anyways.



I heard a wave crash against the shore, not far away.  Long seconds passed.



``If it settles the matter, then fine,'' Calvert said.  He signaled Chariot.



Another Tattletale appeared.  She dropped to her knees the second she materialized.  She wore a similar headset and bindings.



``Free her mouth and one ear.  Be ready to gag her again the second she speaks.''



One of his soldiers approached the kneeling Tattletale.  He undid the gag and freed her ear of the plug that was held in place with wire.



``Rose-L,'' I called out.



``Stringbean-A,'' she replied.  She grunted as the soldier forced the gag back into her mouth.



``She gets to live,'' I told Calvert.  ``If nothing else, you guys are going to need her help to figure out how Jack Slash ends the world in twenty-three months.''



``It's amusing,'' Calvert said, ``That you keep asking me for things I was already prepared to do.  You wanted me to improve the city, to restore it to a working state.  Already planned.  And this?  Killing Tattletale was never in the cards.  I intend to keep her like I do my pet.  Her power will be invaluable.  Rest assured, I will offer every bit of assistance I can when the end of the world approaches.''



``I suppose it was too much to expect that you'd let her go,'' I said.  My heart pounded in my chest.  I wasn't exactly feeling top-notch, so simply standing was feeling like a bit of a challenge.  Fighting back, acting?  No.  No use.  ``Her name is Charlotte.  She's staying in the red brick house a block to the east of my dad's place.  She has a laptop, but she doesn't know what I put on it.''



``Very well.  Men?  Ready-``



``-You're not going to check?''



``Aim\ldots''



``Calvert!'' I said, ``Coil!''



``Fire.''



The sound of the gunshots was deafening, debilitating when I was already missing my sense of sight, my bugs not present enough to give me a sense of the surroundings.  I sensed Grue get hit, then Bentley\ldots I took one in the stomach and folded over.



When the smoke cleared, for lack of a better term, we were still standing.  There was the sound of a few isolated scuffles in the ranks of the soldiers.  My bugs moved to the ends of gun barrels and to the soldiers themselves, noting their postures and positions.



Roughly half of the soldiers that surrounded us were holding the other half hostage.  A few had managed to get shots off, but a quick feel-around with my bugs verified that nobody had been hurt enough to be knocked to the ground.  Most of the bullets had gone over our heads.



``What is this?'' Calvert asked.  ``Travelers-``



``Don't do a thing, Travelers,'' Grue boomed out, in his eerie, hollow voice.  ``Someone remove Tattletale's bindings.''



One of the soldiers approached Tattletale and began undoing the restrictive binding.  She wobbled slightly as she stood, working her jaw in the absence of the gag.



``Glad to see the stringbean plan worked out in the end,'' she said.  ``Those of you I haven't been in contact with, please hear me out.  I'm paying twice what Calvert is for a year's salary, and I'm paying it all upfront.  Look to the other team captains if you don't believe me.  Fish, Minor, Richards, Meck, I've talked to them, and they've agreed.''



There was a slight shift in the tension among the soldiers.  The ones at gunpoint began slowly lowering their weapons, and the ones holding them there similarly let it calm a notch.



``Lies,'' Calvert said.  There was an uncharacteristic degree of emotion in his voice.  ``I've tracked your funding.  I know \emph{exactly} how much money you have.''



``Not \emph{exactly}.  See, I revealed this to my team, just a little while ago, but I've sort of been skimming.''



``From me?''



``A bit.  Not as much as you'd think.  You keep good accounts.  But our targets?  For sure.  Like, we go rob the Brockton Bay central bank, and maybe I skip off for five minutes to go visit the CEO's room, use his computer to get access to more funds, and shift them into a personal account.  Or I keep a few of the more valuable pieces of paperwork, or I pocket something expensive during a job.  Funny thing about a power like mine, it helps me figure out what I can get away with.''



``You haven't taken enough to pay twice what I can.''



``You'd be surprised.  And some of your assets \emph{are} in a position to be picked up by yours truly.  Safe deposit boxes and safes don't mean much against me.  So that's a bit more funding of yours that I can borrow to pay these guys.  A year up front, and I'm not asking them to do a single thing.  Most of them, anyways.  I'm just asking that they ship out of Brockton Bay or they stay on the down-low.''



``I'll pay \emph{triple},'' Calvert said.



``You can't pay triple,'' Tattletale said, stretching as the chains around her wrists and ankles were undone.  ``You've dented your coffers too much with the city revitalization.  Didn't help that you paid such an exorbitant sum to the Dragonslayers for the information they were offering.''



``That was \emph{your} idea.''



``Yeah,'' Tattletale said.  ``You were desperate enough to deal with the Dragon threat before your big show at the debate that you didn't make too big an issue of it.  Either way, you forgot the cardinal rule of employing mercenaries.  They follow the person with the money.''



``I didn't forget,'' Calvert said, ``I had that in mind every step of the way.  I was exceedingly careful of how much funding I provided.''



``Okay,'' Tattletale sounded almost chirpy.  ``But you didn't account for the possibility that I was picking up as much on my own as I was.''



Calvert made a noise that was a borderline snarl.



``Undersiders,'' Trickster said.  ``This goes no further.  Call it a stalemate, but we need his assistance.''



``Calvert's lying, you know,'' Tattletale said.  ``He can maybe help you, but he can't help Noelle.  None of the plans he's been talking about will work, and he knows they won't work.  He wants Noelle for entirely different reasons.  He thinks he can get her on a leash, so he's got firepower even if he gets rid of the supervillains working under him.  A threat that only the great PRT leader Thomas Calvert can address.''



``I'd rather see the truth of that for myself.  You touch him and we kill you.''



``You guys \emph{aren't} wearing the same kind of durable costume we are,'' Tattletale said.  ``If you want to make a point of it, my soldiers can gun you down.''



``I can swap your group with mine the second the gunshots happen,'' Trickster replied, unfazed.  ``You don't want to do that.''



I tried to speak, coughed once instead.  When I finally had my voice, I said, ``Ballistic.  Sundancer.  Any other Traveler with doubts, I know you guys aren't happy with the status quo.  If you want to stop running, stop moving constantly and move to Brockton Bay permanently, we'll have you.  We need you, even.''



A long pause stretched out, then Ballistic stepped forward.



``Hey, man,'' Trickster said.  ``No.''



``I'm done.  This was a doomed quest from the start,'' Ballistic said.  He stopped at Grue's side, turned around to face his teammates.



``Sundancer?'' I asked.  ``You said before that you were lonely, that all of this was too intense for you.  Even the stuff I've done, it didn't sit right with you.  I get that.  Don't you want to stop?  To say goodbye to this life?''



Trickster looked at Sundancer, ``Mars.''



She shook her head.  ``No.  No, Skitter.  I'm staying.  Don't have another choice.''



``Genesis?''



She was in the form of a girl, but wore a simple mask.  ``Someone's got to stay and be a real leader to this team.  No.  I'm standing by Trickster.''



``Teleport me to safety,'' Calvert said.  ``Escort me away, and everything I have is yours.''



``Everything you have is \emph{mine }already,'' Tattletale cut in.  ``You've been dethroned, C-man.  I'm going to rule as the mastermind behind the scene in Brockton Bay, organize the territories, pay the bills.  My partners will see to the territories themselves.  I suppose I won't be head of the PRT, but I'm suspicious we'll be able to work out a truce of sorts with the good guys.  Hopefully we'll get someone more sensible than Piggot and less shady than you.''



``Trickster,'' Calvert said.  ``I can put you in touch with the woman who can cure her.  Someone who knows as much or more about Parahumans than anyone on the planet.  It won't be free, but I can subsidize the costs.  But I have to be \emph{alive} to-``



Trickster collapsed to the ground.  Sundancer and Genesis turned, confused, and Ballistic caught Genesis with a spray of pellets.  She dissipated into gory wisps of whatever substance formed her body.



Sundancer was only just creating her sun when she collapsed as well.  I could see Imp bending over, prodding the bodies.  \"{U}ber, Leet and Chariot backed away as guns turned to point at them.



``Anyone who shoots one of the Undersiders will receive one million dollars!''  Calvert shouted.



I waited for the inevitable bullet.  It didn't come.



``Skitter and I had a little talk,'' Tattletale said.  ``Way back when the city had been freshly sieged by the Endbringer and rejoining the team wasn't even a consideration.  I raised the idea of going after you, of taking you down.  We knew that if you were going to let down your guard, if you were going to slip up at all, it would be when you were closest to achieving your goals.''



Calvert only glared.



``If you made any one mistake, it was keeping me at your base towards the end of the fiasco with the Nine.  The problem with keeping your friends close and your enemies closer?  It puts your enemies in the midst of your friends, so they can discuss better means of payment with the right team captains.  Or they can maybe arrange to put something in Noelle's vault during one of the feeding times, a few fire alarms with a low battery, tucked in where the door meets the wall.  Irritate her, so she's awake that much more, and she then costs \emph{you} sleep.''



``That metaphor fell apart,'' Imp commented.



Tattletale shrugged.  ``Not so much a metaphor, but I got off track.''



``Pettiness,'' Calvert said.



``Strategic.  Lots of little things add up.  Seeding doubts.  Making you second guess plans.  Keep you up at night wondering, planning just a bit more, in \emph{both} your realities.  You were too focused on the big picture, on the thing I could find out, keeping me off-balance, that you missed out on my ability to see the little things, to exploit \emph{them}.  And it wore on you.  You didn't realize how much, but it did, and maybe that's why you were that much more susceptible to making the critical mistake here.''



``Damn you,'' Calvert said.



``But you made the mistake we needed you to make, using your power \emph{here, }while you were talking to us.  There's no escape routes, now.  The only loyalty you have is bought with coin, and I have more cash than you do.''



``Then send me to the Birdcage and be done with it,'' Calvert said.



``To jail?'' Tattletale asked.  ``No, no no no.  I know you have contingency plans.  Arrangements.  We send you to prison and someone breaks you out before you get there.''



I took a step forward, then made myself take another.



``It doesn't have to be you,'' Tattletale told me.



``No,'' I told her.  ``I think it does.''



Calvert turned my way, let his head sink back so it rested against the ground.  ``So it comes down to this.''



I thought of the countless lives I'd put at risk, if not directly, then indirectly: the ABB blowing up parts of the city, the ensuing gang war, Purity leveling buildings because she blamed us for the loss of her daughter.



There was the fat superhero I'd left to die when the tidal wave was incoming.  I recalled leaving the dying Merchant to bleed out when I'd rescued Bryce from the merchant's festival of blood.  There were the people in my territory, the old doctor who'd had her throat cut because I hadn't realized Mannequin was close until it was too late.  The gas attack that killed nearly twenty people and the fires Burnscar had set in my territory, both because I'd provoked them and failed to consider how readily they'd go after the vulnerable point that was all the people I'd been trying to protect.



I remembered trying to kill Mannequin with grenades, going all-out in attempting to end a man's life.  A madman, a monster, but it was what it was.



And, much more recently, there was the case of me bringing Triumph so close to death that he'd needed life support.



I'd come to terms with so much of that by telling myself it was leading to this.  I'd known deep down it would happen.  That my fight against Calvert would have to end here.



I walked forward until Calvert was beneath me.  I drew my gun, checked there was ammo in the clip.



``You're not a killer,'' Calvert said.



``No\ldots'' I replied.  I couldn't see, so I screwed my eyes closed, felt the moisture of tears threatening to spill forth.  I took in a deep breath.



``\ldotsBut I suppose, in a roundabout way, you made me into one,'' I finished.  I aimed the gun and fired.



The gun dropped from my hand as the recoil jarred it.  It clattered to the pavement.  It was quiet enough that I could only hear the ocean water crashing against the shore, just off the beach.



As an afterthought, I kicked the gun a distance away from where Calvert lay.  Not that there was much point.  I tried to learn from my mistakes.



I felt Tattletale's arm settle around my shoulders.  ``We're done.  This is over.''



``The Travelers will be pissed.  I can't- we can't kill them,'' I said.



``We won't.  They'll move on.  They have no more reason to stay.''



Grue stepped around my left side, bent down, took Calvert's cell phone from the man's belt and then tossed it to Tattletale.  As Tattletale withdrew her arm from my shoulders, he stepped forward to give me a hug.  ``Let's go.''



I nodded into his shoulder.



We turned away.  With my swarm sense I was able to recognize Minor, Tattletale's man, helmetless, opening the doors of one van for us.  I took a seat.



It wasn't Tattletale or Grue that sat down beside me, but Rachel.  She took my hand in hers, held it fiercely.  I wasn't sure what to make of it, so I simply accepted it.



\sectionbreak



We stopped at Coil's underground base.  Tattletale's underground base.  It was a relief to escape the silence of the van, surreal to be in the dim noise of downtown again.  Much of the area still lacked power, but there were the noises of the occasional car, of people clamoring on the bottom floor of an apartment building.  City noises.



``You okay?'' Grue asked.



``More bothered by the fact that I'm not bothered,'' I said.  I knew how little sense I was making, but I didn't feel like elaborating.



``But you're okay?''



I nodded, coughed fiercely for a few seconds.



``Our next stop after this is the hospital.''



``Okay,'' I agreed.



As it had been at sunset, the base was empty.  The metal walkway sang with my footsteps as I walked to the far end of the complex.  I stopped at a door without a handle.



``Here,'' Tattletale said.  She held Calvert's cell phone.  Held it up and pressed a sequence of buttons.



The door clicked open.  I forced my fingers into the gap and hauled it open.  Heavy and metal.



There was one more door, one with a key lock.  Tattletale stepped over to the desk and got the key, opened it.



Dinah was inside with an unassuming man in a turtleneck sweater and corduroy pants.



``Go,'' Tattletale told the man.  ``Your boss is dead.  Just go.''



He fled.



``I'm going to get Regent,'' she said.  ``Think we'll leave Shatterbird in her soundproof cage for now, just to be safe.''



I nodded absently.  I was holding on to Grue for support, watched as Dinah stood from the bed and slowly approached.



Her voice was barely above a whisper as she stared down at the ground between us, ``I've been waiting for this for so very long.''



It didn't sound like an accusation.  More the words of someone who had been forced to watch the clock for days, weeks, \emph{months.  }Anticipating a possible moment that might never come.



``I'm sorry,'' I said.  ``I'm sorry it took so long.''



She shook her head, ``I'm the one who's sorry, you were trying hard and I set you up, so you'd go the way where your friends tried to kill you.  I shouldn't have-``



``Hey, it's okay.  It offered us the best chances in the end, right?''



She bobbed her head in a nod.



A second later, she was running to me, wrapping her arms around my midsection.  I winced in pain as her forehead banged against my chest.



``Medical care,'' Grue said.



``For both of us,'' I replied.  ``Dinah and me.''



``Yeah.''



As a trio, we stepped out onto the walkway, where Tattletale and Regent should have been waiting.



But I could see Regent at the end of the walkway, and Tattletale wasn't with him.  She was hurrying down the spiral stairs just to Regent's left.



I leaned over the walkway, as much as I was able with the pain in my chest and Dinah clinging to my midsection.  My eyes went wide.  A moment later, I was hurrying after Tattletale, holding Dinah's hand in one of my own and Grue's elbow in the other.



We stopped when we reached Tattletale.  She stood facing the vault door.  The one that was used to seal Noelle within.



There were \emph{two} vault doors, one set behind the other, and both were ruined, the one closest to us nearly folded in half, hanging by one hinge.



``A final act of spite,'' Tattletale said.  She looked at the phone in her hand.  ``He made sure she heard our conversation.''



``You didn't notice?''



``He was using his ability to create alternate worlds to throw my power for a bit of a loop.  I was more focused on the possibility that he had a loyal soldier in the ranks or a sniper waiting in the distance, ready to take a shot at one of us.''



The odor that wafted from the open vault was like sweat and rotten meat.  It was dark.  Nothing about it gave the sense of a teenage girl's living space.



``On a scale of one to ten,'' I asked, ``Just how bad is this?''



``Let me answer your question with another question,'' Tattletale said.  ``You think we could convince the PRT to turn on the air raid sirens?''





