





\strong{February 2nd, 2001}



The helicopter's rotors stirred up billowing clouds of dust and debris as it landed.



Evan leaned forward from the chopper's passenger seat, hitting the button for the intercom.  The interior of the helicopter buzzed with his voice, ``Check!''



``Clear!''  Lady shouted.  Pyne echoed her.



``Gun up!''  He told them.  He followed his own instructions, unstrapping himself from his seat and collecting his machine gun.



``\emph{Bird one landed, over,}'' the radio buzzed.



He pressed the button, ``Squad two here.  We just touched ground, over.''



``\emph{Waiting on a response from three, over.}''



``Give me a few minutes and I'll be in the air with Pyne for supporting fire,'' the pilot said.



Evan nodded.  ``Wish us luck.''



``Luck.''



He opened the door separating the cockpit from the chopper's midsection.  Four uniforms had been seated in the corners, and were now unbuckled and double-checking their guns and ammo, outfitting themselves with the additional gear that had been tied together and strapped down in the center of the chopper.  Tieu and Coldiron carried the grenade launchers and ammunition: grenades, flashbangs, incendiary and smoke.  Holler and Shane were the guys big enough to haul the extra guns and the packs with ammo clips and supplies.



Pyne and Lady were still kneeling behind the turrets that looked out over either side of the vehicle.  The pilot would be manning the guns for the front.  The pilot, Pyne and Lady were the only ones certified to use the containment foam, the latest addition to the arsenal of the Parahuman Response Teams.



Their entry hadn't been quiet, and he'd expected at least one of the vehicles would see some sign of trouble quickly after they landed.  Maybe it would be the terrified populace of Ellisburg, maybe their target would show up right away.  He hadn't quite expected \emph{this}.  It was empty, a ghost town.  Rain, rain and more rain, not a light on in the small town, not a single soul to be seen.



``Here's the lowdown,'' he spoke to his squad.  Hearing his own voice was reassuring – the only other noise was the drum of rain on the roof of the helicopter and the sound of ammunition clips snapping into place. ``We have him pegged as a high level Changer.  Who can tell me the standard protocol for dealing with a Changer classification?''



``Formation is top priority, trust nothing and nobody, passwords, hit hard and obliterate,'' Holler said, his voice characteristically quiet.



``And for a Changer that's off the charts?''  Evan asked.



There was a pause as his squad tried to recall if this had come up in training.



``Formation is number one priority, trust nothing and nobody, passwords, hit hard, obliterate\ldots and pray?'' Lady asked.



The others all chuckled, some more nervously than others.



``Lady's not wrong,'' he admitted, ``We've been able to piece together who he is.  We got security camera footage from the early stages of the incident, just last week, and we found his face.  One of the top geeks from the Protectorate then found other cases of his face around the city and found a name.  Jamie Rinke.''



His briefing was interrupted as the pilot buzzed them over the intercom, ``\emph{Chopper }\emph{three just landed, cap.  You're clear to move out.}''



``Can we get a picture of the guy?''  Tieu asked.



``No point.  After his first appearance, he started changing his costume for each job, as well as adjusting his body size, body shape and apparent powers.''



``His powers change?''



The captain nodded.  ``Off the charts, I told you.  We've got him down as a tentative changer-seven, trump-four.  The geek was able to dig up some background.  Thanks to his accounting info, credit card statements, phone bills and emails, we know he worked as a banker, made more money than any two of us sorry losers put together.  But he was a loner, no family, no friends, never went out unless it was for the Christmas party at work, and he tended to leave early.''



``So what happened?''



``Got downsized.  Stayed at home for something like three weeks, then the bills started rolling in and he realized he wouldn't be able to pay them all.  He sent out job applications, dozens by email, but he didn't have the references.  Faced homelessness, a disruption of his boring, lonely life.  We think that was his point-zero.''



``His trigger event,'' Lady answered.



He nodded confirmation.  ``Followed by a crime spree.  Span of a few days, quaint little Ellisburg disappears from the grid, communications and power cut, no cars or people getting out.  Guys upstairs sent some heroes in, we got a brief report before they defaulted to radio silence.  Report doesn't tell us anything except they think the whole crime spree was all \emph{the one guy}.''



``And we don't know how he operates?'' Tieu asked.



The captain shook his head.  ``They sent in cameras, cameras got taken out before they got an image.  So they're doing the sensible thing.  They're sending \emph{us}.''



``Great,'' Coldiron said, his voice thick with sarcasm.



``We're not alone out there, so be careful about where you're shooting.  This place's got a population of about five thousand.  Sort of town that has only the one movie theater.  But whatever this bastard Rinke is doing, we think he's operating from somewhere near the middle of the area.  Three helicopters in the air, three squads of six, and a team from Toronto's Protectorate division backing us up.  We move in a spiral pattern to close in on the center of this podunk town, see if we can't squeeze him out of hiding, and we maintain radio contact with the other squads at all times so everyone knows what's going on.''



Lady had started pulling on her pack, with others watching out the tinted window around the turret.  She buckled it on and then gripped the hose-sprayer.  The display on the nozzle would be showing her the amount of foam remaining, as well as the settings for spray volume and distribution.  She gave him a thumbs-up.



He gave her the smallest of nods.  ``Let's move out.''  He raised his radio to his mouth, ``Squad two moving out.  Where's our capes?  Over.''



``\emph{Capes are with squad three, over.''}



``Pass on word if they break rank.  I really don't want to shoot a friendly, over.''



``\emph{Will do, over.}''



He hit the button, and the side of the helicopter folded up.  Moisture from the rain dotted the flat expanse of his helmet.



He was point, Holler and Tieu covered the right and left flanks, Shane and Coldiron covering their rear.  Lady stood in the middle of the group, ready to lay supporting fire where it was needed.  Their gun-mounted flashlights were the only light outside of the scant amount that filtered through the clouds.



The streets were empty.  Cars had been abandoned where they were, doors left open, windows broken.  There was no blood, no bodies, no clothing strewn about.  Here and there, things had been knocked over, but that was all.



``\emph{Nobody} evacuated?'' Tieu asked.



``No,'' the captain replied.  He wiped the water from his helmet with the crook of his elbow.



``Then where'd they all go?''



``I suspect we'll find out.''



They passed a store with a grinning deer on the logo: a `Mister Buck' store.  Signs proudly proclaimed that everything inside was a dollar.  It was the kind of cheap carry-everything store that appealed to the lowest common denominator, but in a town this small it was the centerpiece of the `downtown' area.  The front window had been shattered, and various gardening implements were scattered around the interior, out of place; hoes, shovels, pitchforks.  \emph{Improvised weapons?}



``Holler, anything thermal?''



``It's cold.  Rain isn't helping, but I'm not seeing anything except you guys.  Not even a smudge in the darkness''



They moved on, guns trained in every direction, eyes scanning the area for their target.  They passed a clothing store, where the window had been broken, the contents of one rack strewn out in the street, plastered to the road with the rain.



Evan picked up the radio, ``Squad two here.  Anything out there, boys?  Anything at all? Over.''



``Nothing at one, over.''



``Ditto from three, one of my squad just said they're not seeing any critters.  No birds, rodents or strays.  Over.''



No animals, no people.



``We're taking a short detour,'' Evan informed his squad.  He pointed with his gun, ``This way.''



His squad took cover beneath a bus shelter that was attached to a nearby storefront.  The panes of plexiglass had been broken, but the overhang offered respite from the rain.  He adjusted his flashlight to increase the light output and pointed it straight down at the ground.



``Sir?''



``One minute.  Keep your eyes peeled.''



Long seconds passed.  He changed the settings on his flashlight back to normal.



``What was that about?''



``No bugs.  Dark night like this, you'd think there'd be a moth or some mosquitoes gathering around the light.''



``Captain,'' Holler spoke up.  ``Something on the thermals.  Dim.''



They turned to face the same direction as Holler.



``Coming around the corner,'' Holler spoke.



``Lights off,'' Evan hissed the order, clicking off his flashlight.



In a second, the gun-mounted flashlights of his squad members flicked off.  The shape that moved down the street was reduced to a dark blur, a shifting bulk of gray-black against a background of pitch black.



\emph{Rinke?}  As his eyes adjusted to the darkness, he could make out a figure dressed in a jester's motley, two contrasting colors predominating, blue-orange or purple-yellow.  The mask a patchwork cloth that covered his face, with only two dark holes for his eyes.  But most daunting of all was the man's size.  He was obese, bloated, ten feet tall and nearly as wide, advancing at a glacial pace as he lurched down the middle of the street.  His arms were drawn behind his back by the weight of the sack and the cloth he carried.



He raised his radio, clicked it on.  In a low voice, he spoke, ``Got eyes on Rinke.  He doesn't see us.  Move in to our location to support and keep the radio quiet.  Over.''



There was a confirming buzz as the man on the other end turned the radio on but didn't speak.  \emph{That would be squad one.}  Three buzzes marked squad three's response.



``Strategy?''  Tieu whispered the question.



``Wait for the other squads.  Foam him, burn him to ash with an incendiary.''



``We're not going to interrogate him?  Find out what happened to the people here?''  Tieu asked.



``No,'' Holler was barely audible.  ``He's got no heat.  The reading came from the bag.  Not warm enough to be alive, but whatever's in there's just warm that it was probably living up until a few minutes ago.''



Every eye in the squad turned to the large patchwork sack that the bloated \emph{thing }hauled behind it.



``Not worth the risk to interrogate,'' Evan murmured to his squad.  ``We foam him, which shouldn't be hard with how slow he's moving, then we burn him because that's protocol for dealing with Changers.  We'll do it quickly and without hesitation because he's got a Trump rating as well.  Don't know what cards he has up his sleeves.  Might want to disappear us like he did with the rest of the locals.''



``And the wildlife.''



``And the local wildlife, yeah.  Safeties off.''



Rinke slowly turned to face them.  The second the dark holes of the mask centered on them, they opened fire.



Evan's entire body shook with the recoil of his assault rifle.  The brute didn't seem to mind as his blood and flesh sprayed from the holes the bullets opened up, advancing steadily.



Tieu and Coldiron fired the incendiary grenades.  The shells exploded on impact with Rinke and the ground, lighting him up.  He continued to waddle towards them, slower than they were able to walk backwards.



Rinke dropped the sack, gripped the sheet with both hands and hurled it towards them.  It spread out, scant amounts of light filtering through the holes in the weave.



\emph{A net}.



Lady shot the net out of the air with a blast of foam, causing it to land at the halfway point between them and the brute.  She sprayed his feet, locking him down to the ground.



Rinke thrashed as the flames spread.  The cloth burned away to show pallid, gnarled flesh, a face without ears, nose or brow – only recessed, piglike eyes and a mouth that was little more than a ragged gash across the lower half of his face.



``Another incendiary, everyone else hold fire!''



One more incendiary shell struck home, ensuring the monster was covered in flame from head to toe.  The smell of burned meat and sulphur filled the air.



``Hold position!  Wait for the fire to do its work!''  He raised his radio.  ``We engaged and foamed the bastard.  He's lit up.  Over.''



``\emph{Squad one hears you, over.}''



``\emph{Squad three here.  Good work, over.}''



The bloated stomach split with the weight of the upper body, tearing across one of the recesses of a roll of fat.  A slurry of half-dissolved bodies spilled out around him.



``Tieu!  One more!''  Evan called out.



Tieu fired an incendiary round into the opening, lighting the brute up from within.



It took several minutes for the entire thing to burn.  They didn't relax a second.  It was the number one lesson drilled into them in training: as regular humans, it was a given that they were the underdogs.  That meant that no matter how well equipped they might be, no matter how weak the enemy, they were not allowed under any circumstances to give the enemy an advantage by underestimating them.



``Hold position,'' he warned.  They'd wait until the others arrived.  Rain pattered on the roof of the shelter, and fire crackled and hissed as it turned the mass of flesh into crumpled black tissue.



The sound of distant gunfire cut through the quiet.



``What?'' Holler asked.



Evan spoke into the radio, ``Hear gunfire.  Report, over.''



The response came back, ``\emph{Hostiles!}''



There was no `over' to mark the end of the transmission, only more gunfire.



``Move out!''  Evan ordered his squad.  Into the radio, he shouted, ``Squad two coming in to reinforce!  Over!''



Squad one had surrounded themselves with a ring of containment foam, and were alternately scanning the surroundings with their flashlights and firing bursts into the shadows.



Two members of squad one dropped as spears of bone sank into the armor at their chest and neck.  Evan caught a glimpse of the attackers, waist-high figures with oversized heads.  Two had mouths like the bloated thing had, with the narrow teeth of a fish, while a third had a beak.



\emph{That wasn't Rinke we shot.  There's others}.



The other realization hit him just as hard.



``He's not a Changer!''  Evan bellowed, clicking the button of his radio to inform the capes and squad three.  ``Master-class cape!''



``Sir!''  Shane shouted.



Evan turned.  There were more crawling out of the windows and storefronts behind them.  They ranged across the spectrum of body sizes and shapes, from small men little more than knee-high to figures not unlike the bloated thing they'd attacked earlier.  Males and females, fat, thin and muscular, tall and short, nearly human and almost alien.  Two or three dozen of the assorted creatures.



No.  He caught sight of light reflecting from watching eyes in the shadows, eyes that reflected light like a dog or a cat, in the darkness of building interiors and the shadows of alleyways.  There were quite a few more than two or three dozen.



``Fighting retreat!  Fire at will!''



They backed towards the other squad.  Their gunfire mowed through the enemy, the grenades killing ten or more in a single detonation, but the enemy ranks were seemingly endless, the targets too unpredictable. Some were slow, others fast.  Some made large targets, absorbing gunfire meant for their fellows even as they died, while others were damnably small.  The mass of them made noise, too, squealing, gibbering, giggling and grunting.



\emph{How did he do this?}



Squad one had no doubt laid down the containment foam to stop the ones that were small and quick enough to avoid most gunfire, but they'd trapped themselves in the area, and were now falling prey to the hail of spines.



Coldiron took one spine to the face.  He dropped like a puppet who'd had its strings cut.



\emph{The standard PRT-issue suits are supposed to sustain gunfire.  Those spines are hitting harder than bullets.}



Rinke was a master who can make these things: real living creatures.



He cast a glance at squad one, down to one member, kneeling with one arm around a teammate he was using as a body shield and the other hand firing his rifle one-handed.



``Retreat!  Through the store!''



His team ducked back into a storefront through the shattered display window.  Bursts of fire took down the creatures that had been hidden within, a skinny faceless woman with blades for fingertips, a trio of what looked like babies with spider legs, a half-dozen waist-high people with deformed features and mismatched clothing that they'd clearly scavenged from nearby.



While Shane and Tieu reloaded, he offered supporting fire.  He gunned down one of the smaller creatures, caught a glimpse of one of the other thing's expression.  It was female, small, and its face twisted further in rage than it had already been.



\emph{They feel.  They have feelings?}



The horrible thought that they might be people crossed his mind.  The notion that this was a psychological trick, that he was under the influence of a power, gunning down civilians\ldots



No.  He'd been trained to deal with mental and emotional attacks.  They all had.  Had to think abstractly, consider the edges of the problem.  Even if their perceptions were under attack, there were always hints, always clues.  Things matched too neatly.



If this \emph{was} a trick, it was complete and effective enough that they were already doomed, no matter what they did.



His squad headed out the back door of the store, gunned down a tall creature in the alley as they made their way to the next street.  Their gunfire brought more of the things crawling from the woodwork, throwing themselves down from windows and crawling out of the spaces in dumpsters and beneath cars.



``Flare!''  He shouted.



There was a brief whistle as the flare speared up towards the sky.  As if in response, one of the beasts perched in a windowframe spat a glob of caustic goo at them.



Shane went down screaming, smoke pouring off him as his suit was consumed and the acid reached his flesh.



They couldn't afford to stop.  Evan fired a single bullet through Shane's skull without slowing his run.  Holler got the thing in the window.  It exploded violently, globs of acid spraying through the area to steadily eat away at the surrounding architecture.



Evan reloaded, all too aware of how quickly he was going through clips.  Lady was covering their retreat with foam, but the foam would run out.



One of the helicopters had approached, laying down additional foam to help.  There were no safe places here, no places to find cover.  The best they could hope for was to get to a spot they could evacuate from.  There wasn't a living soul left in the city, nobody to save.



The sound of the explosions had drawn the attention of others.  They were pouring from nearby buildings.  Concentrated rifle fire tore through their ranks, but did little to stem the overall tide.



``Captain!''  Lady shouted.



He turned to see that she was all right, then saw what she was pointing at.  One of the things, a pear-shaped woman with thick legs and no arms, was standing with her legs shaking from strain as she virtually spewed a mess of creatures out onto the ground.  They clawed and bit their way free of the sacs that held them and wasted no time in starting to crawl, lurch and run towards his squad.



Holler gunned the mother-thing down before she could finish or spew more abominations from between her loins.



Things were clicking into place.  It made sense, now, how the situation had gotten out of control so quickly.  How Rinke had seized the city so totally and absolutely.  It wasn't just that he was a master-class cape who could make monsters with abilities of their own.  He could make monsters that bred, monsters that gave birth to more monsters.



``Flare!''



Holler fired another flare into the sky.



Evan reached for his radio, shouting at the top of his lungs to be heard over the gunfire, even his \emph{own} gunfire.  ``Squad two needs an evac, stat!  We just sent a flare up!  Where are those capes!?''



``\emph{Choppers one and two down, squad two.  Your capes vacated the scene.}''



``Damn them!''  He pointed his gun to the sky to gun down an emaciated winged beast that was trying to swoop down on them from overhead.  ``Get us chopper three, then!''



``\emph{Chopper three is giving squad three supporting fire while they all retreat to a viable landing point.  You'll have to get to them.  They're north of your position.}''



``You heard the man.  Move!''



They didn't get two paces before the ground rumbled.  A clawed hand speared up through the pavement to catch Tieu by the leg, crushing it as though it was paper.  The pavement strained and cracked as whatever was beneath tried to break the surface.



Tieu looked up at his team, his expression hidden by the pane of his helmet, then stuck the end of his grenade launcher into a crack in the concrete.



They were already running, their backs to him, when the explosion marked the loss of another member of their team.



A grenade round cleared away one more crowd, and they hurried through the gap.



\emph{Three of us left.}



Without Tieu or Coldiron, they didn't have a grenade launcher, no way to deal with the massed crowds.



``Holler, need ammo!''



Lady directed a stream at the nearest crowd, aiming the spray at their heads, so any spray that missed would catch the ones who stood behind them.  When one tipped forward, the expanding foam served to create a barrier that caught others.



Holler pulled off his bag, handing out clips.  Evan tucked away the ammunition as fast as it entered his hand, pausing only to reload and shoot down the creatures closest to them.



He turned his head as he heard a voice.



``-Eat!  Eat!''



``Go!''



They'd defaulted to a three-man squad, Lady covering the left and some of the rear, Holler watching the right and the rest of the rear, with Evan leading the way.  The voice\ldots



A laugh.  Not the gibbering noise of the creatures, but all too human.



He spotted the culprit.  A man, potbellied and hunchbacked.  The style of dress was similar to the patchwork brute they'd fought first, with bright, contrasting colors that he couldn't quite make out in the gloom.  There were jarring patterns with stripes here and checkers there.  He wore a cloth crown, and his cloth mask featured beads for eyes and a perpetual leer of a smile.



\emph{Rinke.}



``Rinke!'' he screamed the word.  He took aim and fired.



He hit his mark.  The man went down, and the creatures wheeled on him, screaming, squealing.  If he'd had any doubt about his target, the reaction dispelled it.



Then he saw Rinke stand.



``You would shoot me!?''  Rinke roared.  If anything, his voice was all the more terrifying because it sounded so small, so human.  ``I create life!  I am a god, and this is my \emph{garden}!''



Evan could see flesh billow into existence in the man's hands, embryonic sacs with the shadows of something forming within them.  They burst, and two struggling, childlike figures dropped to the ground to disappear in the midst of the stirring crowd.



Lady did what she could to suppress the enemy's approach, laying down the foam, but there were too many, and their irregular sizes and shapes made it impossible to cover all of them with the foam.  If she aimed high, she missed the little ones.  If she aimed low the bigger ones leaped over and others walked on top of the ones who'd become stuck.



A spine caught him in the midsection.  Before he could react, another struck home.  They penetrated his armor to stab into his stomach like hot knives.  He caught a glimpse at one of the bastards that was spitting the things at him, gunned it down before it could shoot again.



He could hear the helicopter's approach, knew it was too late.



``Ring!'' he gasped out the word.  He could barely breathe, felt like a weight was sitting on his chest, every word he uttered came out thinner than the last.  ``Circle us, make high.''



Lady did, laying down foam in a circle around the remnants of his squad.  He couldn't breathe at all, now.  Had one of the spines caught him in the diaphragm?



He was blacking out, faster than he'd expected, saw the bastards making their way over the top of the wall of foam, getting stuck, others using their bodies as handholds to crawl forward, reaching, drooling, screaming, squealing.



Didn't matter.  He was dead anyways, knew it beyond a doubt.



One of his squad members collapsed on top of him, blood spraying out onto the front of his helmet.



The darkness took him.



\sectionbreak



`Lady' stirred, felt the weight of machinery and tubing that kept her from moving.



``You're awake,'' an unfamiliar voice called out.



She tried to speak, couldn't.  Her throat was raw, her tongue leaden.



``I don't want to offend you, but I'm frankly surprised you made it,'' the man spoke.  She turned her head to one side to see a bed in the other corner of the room.  A tall man lay there, hooked up only to a saline drip.



``I'm Thomas Calvert,'' he introduced himself.  ``Squad three.  We're the only ground forces that got out alive.''



\emph{The only ones}\ldots  She shut her eyes.



``Your sister was here.  She was talking to the doctor about your prognosis.''



``Pro-'' she started, wincing at the pain speaking caused her, ``Prognosis?''



``You might not want me to tell you.  The doctors will be gentler than I will.''



``Tell me.''



``Deep tissue damage.  Your kidneys are gone, which means you may be on dialysis for the rest of your life.  You suffered some muscle damage when they gnawed on your legs.  There's no future for you on the PRT teams.''



She shut her eyes.  She'd lost her squad, her career, her health, all in a matter of an hour, if that.  Half an hour?  How long had the mission taken?  Twenty minutes?



``You're not alone.  I won't be joining any future missions either,'' Thomas remarked.



``Rinke?''



``You mean Nilbog.''



``Huh?''



``That's what he called himself.  He's alive and presumably well.  I saw out the window as the chopper pulled us out, Nilbog retreating to hide in some building, his creatures were returning to their hiding places.  I expect the man will be alive for some time.''



``Why?'' She wheezed the question.



``Far as I could tell, he's wearing one of his creations.  Made him bulletproof, maybe fireproof.  We won't be able to bomb the area.  He's created beasts that multiply if you set them on fire.  Did you see those?''



She shook her head.



``He may have other countermeasures for other courses of action.  You'll get your chance to talk to the Chief Director, but last I heard, they're planning to wall the city off.  They'll let the motherfucker be the god of his own little town, so long as he doesn't try to expand any further, which they're saying he won't.  I almost envy him.''



``He\ldots gets to live?''



``Yeah,'' Thomas spoke, letting his head rest on the pillow.  ``It is a perk of having power, that you get to decide which rules apply to you.''



She shook her head.



He sighed.  ``I thought I might trigger, perhaps.  Hoped.  I suppose I don't have the potential.''



She glanced at him in surprise.



``What?''



``I\ldots I'm glad I don't have powers.  That I \emph{can't} have powers.''



``\emph{Why}?''



``They're monsters.  Freaks\emph{.  Lunatics. } They fight only because they have the impression that they're stronger than their opponents, and when they aren't they run.''  She thought of the squad of capes that had accompanied them. ``They abandon the rest of us.''



Thomas chuckled, and it sounded \emph{mean}.  Mocking.



``What?''



``I suggest you change your attitude,'' he said.



``Why?''



``It's ironic.  When the doctor and the Chief Director were talking to your sister, the Chief Director assured her that you still had a position in the PRT.  Some of it is probably to keep you quiet, a cushy desk job and fat paycheck to make up for the fact that they sent you into a deathtrap and killed your teammates.''



``A desk job?''



``Director.  You'll manage the local teams, handle the PR, convince everyone else that they \emph{aren't} freaks, monsters, lunatics and bullies.  I suggest you fake it, pretend you really do believe it.  You might start to believe your lies.''



``And you?''



``Oh, I did mention I wouldn't be on the team in the future.  Not because of any injuries, mind you.  I'm facing a stay in prison.  My captain and I were the only ones left,'' Thomas knit his fingers together and rested them on his stomach, looking very calm.  ``He grabbed the rope ladder first, but he didn't climb fast enough.  I shot him.''



Her face twisted in disgust.



``You would have done the same in my shoes.''



``Never.''



``Well, it doesn't matter.  A few years of my life.  I don't expect I'll be there for too long.  There \emph{were} extenuating circumstances, and the PRT doesn't want me talking to anyone about what happened.''



She shut her eyes, tried to shut her ears to his smooth voice prattling on with things she didn't want to hear.



Monsters, freaks, lunatics and bullies\ldots the labels didn't belong to just the capes.



\emph{It's like the world's gone mad, and I'm the only sane person left}.





