





``Holding court?''  Cinderhands asked.



``We've waited long enough,'' Marquis answered.  ``Word's out, demand's high, and it's hitting people harder because they've been thinking about it.  The time is right, if you're ready, Amelia?''



Amelia stared down at her hands.  ``I don't want to.''



``Life is full of things we don't want to do.  I won't force you, but I think you and I would be \emph{very} well served if you stepped up to the task.  It will be harder to protect you if you don't.''



Amelia frowned.  ``You mean you'd throw me to the wolves.''



``No.  \emph{No}.  If you \emph{truly} decided that you couldn't, if the situation forced an ultimatum, I would give up the power I have as the leader of Block W if I had to.''



``I can't tell if you mean it.''



Marquis took his time rolling and lighting a cigarette, then kneeled before her.  He spoke with it bobbing in his lips, ``My girl.  I'm not a good man.  I have rules I follow, but that doesn't make me \emph{good}.  At best, it's one virtue among many I've failed to acquire.  I'm rough around the edges, whatever I might play at, and that's plain enough to see to anyone who pays attention.  I grew up in hard circumstances, and it's taken me a long time to work past that and earn the respect I get.  And I would give that up if you needed it.''



``You don't \emph{know} me.''



``You're family, Amelia.''  He stood, pulled the cigarette from between his lips and kissed her on the forehead.  He didn't miss how she pulled away in alarm and surprise.  ``Whatever else, that's the most important thing in the end.''



He let the words sit with her, turning away.  Lung stood by the door, arms folded, and Marquis smiled lightly at the man.  \emph{He'll see this admission as weakness, but the right display of confidence will leave him wondering if it's a lie, a ploy.}



Lung, much like all of the other prisoners, was wearing the gray cotton clothing that was supplied regularly through the drops, alongside the other essentials.  He'd torn off the sleeves of the shirt, showing off muscular arms that were emblazoned with tattoos down to the fingertips.  The light brown of his eyes was surrounded by an expanse of bloodshot red instead of whites.  Other than his muscular physique, they were the only thing that set him apart from any ordinary man who one might see on the streets.



Lung was a killer, a wild animal who played at being a man.  Marquis had picked up enough details to know Lung's story.  He'd broken the rules, broken the code, because he'd thought he had the power to get away with it.  But it had been a power he couldn't quantify, a blend of raw military strength, reputation and circumstantial power.



Just as there were athletes who studied their sport, trained their technique and honed their bodies with specific goals in mind, there were others who drew from natural talent and instinct.  Lung had built his gang by conquering others one by one, going by his gut to identify those who would stand in his way and then violently removing them from his path.  His instinct and a tenacious power gave him his success on the street level, where he seized control of the local drug trade, of soldiers, but they hadn't fared so well in the scope of a greater war.



And so it was that Lung found himself here.  Among the fallen, so to speak.



He turned his attention to Amelia.  His daughter.  She sat on the edge of the bed, slouching forward.  Her clothes weren't torn or modified, and her sweatshirt was a fraction too big for her – she was staying in his cell block, and the clothes were meant for men.  For the time being, she was being left alone.  He'd asked the men of his cell block to look after her, and because of this, she was afforded a certain respect.  People got out of her way, not because they knew anything about her, but because they knew \emph{him}.



It was precarious and unconventional.  A girl in the men's cell blocks.  It wasn't new, exactly, some had taken wives, had girlfriends or paid girls to serve them as prostitutes.  But Amelia was someone with no confidence, no presence, giving every sign that she was a \emph{victim} rather than a warrior.



This wouldn't last.  The men in the Birdcage were still \emph{men} in the end, and they were men who'd found their way here because they had \emph{defied} the system.  Some, like Lung, had broken the unspoken codes, others had challenged authority and lost, while others still had simply broken the rules too many times.  It was a matter of time before they lost patience with Amelia after devoting so much time and effort to protecting someone who didn't have anything to offer.  Or they would challenge Marquis; any number of maneuvers ranging from overt mutiny to subtle sabotage.



``Are you holding court, then?'' Cinderhands asked, once again.  The man had a shock of red hair that was shaved on the sides, and holes in his nose and ears that pointed to old piercings, only some of which had been replaced by rings and bars hand-crafted from scraps of metal here in the `cage.  His hands and arms were a burned black up to the elbows, more like a used log gone cold in the fireplace than flesh.



``I'll hold court.  Amelia can sit in.''



``You sure?'' Cinderhands asked.



Marquis turned to stare at the young man, drawing in a lungful of smoke from his cigarette, ``You've never questioned my decisions before.''



``Your decisions haven't raised any questions before.''



``Watch yourself,'' Marquis said.



Cinderhands narrowed his eyes and pursed his lips, but he nodded slightly in acquiescence.



``Go pass on word, let the other block leaders know.  I'll hold audience for one hour, starting one hour after the next shipment arrives, ending at lights out.  First come, first serve.  They can come themselves or send a representative.  We won't challenge their passage, but no more than two from a block.  Stay by the cell block gates and keep an eye out for trouble.''



``I'll need some guards if you want me to \emph{do} anything about that trouble,'' Cinderhands said.



``Then find them.  Or tell me you can't, and I'll find someone else to handle the job,'' Marquis let his annoyance seep into his voice.



Cinderhands stalked off.



How long before they confronted him?  There was a difference between being someone strong enough to be left alone and being leader of a cell block.  Lung was the former, he was the latter.



That said, his \emph{real} worry was that they would attack him indirectly, standing by while Amelia was hurt, or failing to back him up at a crucial moment.



In fact, he was giving serious thought to the idea of provoking a mutiny among his people.  A solid and undeniable victory would remind people of why he was leader of Cell Block W and help to root out any of the more conniving individuals who were plotting a more subtle form of attack.  That is, if they were impatient enough to capitalize on the ensuing chaos.



Actually being defeated, it wasn't really a consideration.  He'd only lost a fight on one occasion, and those had been extenuating circumstances.



In any event, instigating a mutiny would only serve as a stopgap measure.  This was a problem he needed to address at the root.  Amelia.



He glanced her way.  She hadn't moved, and she was still staring at her hands.



She wasn't the first of her kind that he'd seen.  A hollow shell.  Tabula rasa.  A blank slate. She wasn't sleeping at night, not easily, and she had frequent nightmares.



He'd seen others, had had two appear in his cell block, delivered by their tinker overseer.  Except he wasn't a nurturer.  He had no experience on that front.  He'd done what he could to see if he could wake them up from the neuroses that gripped them, and then he'd bartered them away to other cell blocks when he hadn't seen improvement over one or two weeks.  People who were damaged on this fundamental level tended to go one of four ways.  They recovered, which was rare; someone filled the empty vessel with an ideology; they were used as a resource, cared for so their talents could be exploited; or they were spent, burned up of whatever they had to offer, be it making things or violence.



He wished he'd tried his hand at fixing the two who Dragon had delivered to his block.  Maybe he'd have a better idea of how to deal with Amelia if he had.



``We have twenty minutes until they start arriving.  Go shower, Amelia.  Make sure your hair is dry when you return, and don't wear a sweatshirt.  They envelop you, make you look like you're hiding.  A short-sleeved shirt will do.''



She stood and headed out the door, her slippered feet slapping as she walked.



He could have escorted her, but he didn't.  It would be better in the short-term, but more damaging to their image in the end. Instead, he ventured out of his daughter's cell, standing at the head of the railing for the raised area that overlooked his cell block.



There were thirty people in Block W, including himself and Amelia.  Those thirty people shared five televisions with no remotes, two weight benches, one open area for general exercise and sports, and a seating area with tables and benches.  The cells themselves were arranged in a horseshoe shape, encompassing the area, with two gently sloping ramps meeting at the furthest cell, his own.  Beneath his cell was a corridor that led to the supply delivery area and the showers.



Tidy in appearance to the point of caricature, Spruce stood guard by the televisions, helping ensure that Block W remained the only block with a full set of working sets.  He would ensure everyone had a turn to choose the channel.  Whimper was overseeing the auction.  Everyone had already received their share of the cigarettes, which served as currency for bidding over the more in demand items of the supply drop.  There were less new blankets than there were people in the block, for example, and each drop only included maybe three or four books; always one classic and two from the recent bestseller's lists.  Good reads and books with raunchy scenes could be resold to other prisoners for a decent amount, and they would exchange hands until they were too worn to keep.



From his vantage point at the railing, Marquis could see most of the way into virtually every cell in the block.  Only the cells at the very end were at the wrong angle, and he'd stationed his lieutenants there.  His lieutenants and Lung.



Not every block worked the same way, though the layout and the scheduled drops were the same for each.  The advantage of Marquis' arrangement was that it kept his people relatively happy and it kept them in their place.  The lieutenants and Marquis himself got first pick of any of the items from the supplies, but nobody truly went wanting, so they generally agreed with minimal complaint.



He watched Amelia make her way to the point on the ramp where the railing terminated, step down to the corridor below that led to the showers .  He could see the glances that were directed her way, some almost animal, \emph{hungry}.  Others, almost more alarming to that part of himself that he associated with fatherhood, were cold, measured and calculating.  More than a few sets of eyes belatedly turned his way after looking at his daughter, as if gauging whether he was noticing that \emph{they'd} noticed.



By way of response, he called on his power, generating twin spikes of bone that crossed the end of the corridor in an `x'.  Amelia passed through the gap, crouching slightly, and he filled the remainder of the space with branching lengths of bone.



Even the littlest things were a hassle, now.



He snapped the bone, keeping his expression blank in the face of the mind-shattering pain that resulted.  It faded quickly, and he let the remainder of the bone fall to the floor, joining countless other shards and fragments around the mouth of his cell.  It invoked a mental picture of a lion's den.



This was a gamble.  Amelia could be the excuse his enemies or more ambitious underlings needed to mount an attack.  At worst, he'd die and she would\ldots well, she'd be a resource that was burned up, exhausted of anything and everything she had to offer.  If he was able to buy enough time, verify that she was beyond saving, then he could return her to the women's cell blocks, cut his losses and take the resulting hit to his reputation as the only real cost of trying.



He didn't want to take either of those options.  He had so few memories with her, from when she'd been a toddler, but they'd stayed with him.  He remembered the sparkle in her eye as she saw the princess costume he'd had tailor-made for her.  He recalled the look of consternation on her face as she'd sat at his dining room table while she practiced writing her letters.   That frustration had become awe as he'd showed her what she could accomplish once she mastered the art, penning out florid letters in cursive with a fountain pen.



More than once, as he prepared tea to share with Lung during one of their long discussions, he'd thought of the mock tea party he'd had with his daughter.



Those moments seemed farther away now than they had in the days before he'd been reunited with her.  He would never recapture them, he knew, but maybe he could find other, new memories to share with her.  A deep conversation, a father's pride at her accomplishments.



Before that was possible, he had to resolve this situation.  Fixing her was too lofty a goal.  Cementing his own power base would do as a short-term goal.  He would need to show his people and the other cell blocks that there was a reason why he'd invested this much attention and effort into his daughter.  To do \emph{that}, he would have to decipher the puzzle of her psyche, figure out a way to coax her into demonstrating her power.



He was running out of time, judging by how his followers were acting.



``You will be disappointed if you expect my help, Marquis,'' Lung's low, heavily accented voice came from behind him.



``I know.  You're your own man.''



``I had more respect for you before \emph{this}.''



\emph{Before my daughter.}



``You and everyone else here.  It's a shame.  I'd hoped I'd amassed enough credit that you and the rest of them could trust me to see this through to a successful conclusion.''



``Mmm,'' Lung rumbled.  ``Do \emph{you} trust that you'll see this through to a successful end?''



Marquis didn't trust himself to lie convincingly, so he only smiled.



``You do have a plan?'' Lung asked.



``You'll see,'' Marquis replied.  ``Will you be attending the meeting?''



``I am not one of your lieutenants.''



``But you've earned yourself a reputation in a short span of time.  That's commendable.''



``No flattery.  Get to the point.''



``It helps us both if you're there.''



``You look more powerful if you have the mad dog on a leash,'' Lung growled.



``Some may see it that way.  I won't deny it.  But in \emph{my} perspective, you're dangerous, and people will notice if I'm unconcerned about having you loose in my block.''



``You're insulting me.  Saying you look down on me.''



``No.  I'm stating the facts.  Yes, in a straight fight, maybe you could give me a run for my money.  Maybe not.  But I have my underlings, and that leaves me fully confident I'd win.''



``You might not have those underlings for much longer if this continues.''



``I notice you're not disagreeing.''



Lung offered a noncommittal grunt in response.



``If you stay,'' Marquis said, resting his elbows on the railing, ``You can meet the other cell block leaders, get a head start on figuring them out for when you've murdered me and taken over W Block.''



``You don't sound concerned.''



``Someone's going to try, Lung.  Someone's going to succeed.  Might be in two years, might be in five years, or ten-''



``Or today,'' Lung cut in.



Marquis waved him off.  ``Not today.  But it's a fact that it'll happen \emph{someday}.  I'd rather it was you, when that day comes.''



Lung's eyebrows rose in a rare expression of surprise.  ``Why?''



Marquis stood, stretching, and tossed his stub of a cigarette to the corridor below.



``You can't imagine I'd be a kind or generous leader.''



Marquis laughed.  ``No.  But wouldn't you rather be murdered by a rabid wild beast who happens to share your living space, than to have a onetime ally stab you in the back?''



``It doesn't matter,'' Lung replied.  ``You'll be dead either way.''



Marquis gave the man a slap on the shoulder.  Lung tensed, more because of surprise at the abrupt, familiar gesture than anything else.  Marquis sighed.  ``There are times I envy you.''



He turned to head down the ramp, descending into the crowded area where supplies were being sorted.



Whimper showed him the books.  A murder investigation novel, a young adult story featuring some romance with a ghost, a book with a bird mask on the cover and a Dickens novel.  Marquis selected the last.



He seated himself on a bench where he had a view of both the corridor and the cell block entrance.  While others cleared out of the area, Marquis glanced up at Lung, who still watched from the railing above.



He turned his attention to the book, pretending to read while thinking over the situation.



\blacksquare



He glanced toward the door of bones in time to see the shadow of Amelia's approach.  Controlling his own `dead' bones was harder, but he'd been standing at the ready to demolish the barrier, and pulled it down before she got there.



``You took some time,'' he said.



Amelia hugged her arms to her body.  ``I sat down to think and lost track of time.''



``We're worriers, my girl.  It's an asset when applied in the right amount.  Is your hair dry?''



Amelia touched her hair but didn't venture a reply.  He reached out to touch her hair, and again, he saw her flinch.  ``Good enough.  Have a seat.  The latest, what was it, a novel from this `Fade' series?  It was there for auction.  I could send someone to track it down if you're interested.''



She shook her head.



``Not interested in reading, or not interested in reading \emph{that}?''



``Both.  Mostly the second part.''



``At least you have taste.  Well, the meeting begins in one or two minutes.  I would like you to attend, of course.  Best if you don't speak unless directly asked a question, and say less rather than more.  It's a tactic I employ myself, leaves you less room to say the wrong thing.''



``They're going to ask me to use my power.  I can't.''



``I understand.  Yes, they probably will want a demonstration.  I only know what Lung's told me, which isn't much, and what you've said, which is even less.  That in mind, I still think that a demonstration would do a \emph{great deal} to secure our position.''



``I can't,'' her voice was small.



\emph{Then we may well die, my daughter}.



``We'll cope some other way, then,'' he said.  ``In the meantime, to convey the right image, it's best if you make eye contact and speak clearly.  Sit.''



``Okay.''



He stood, then seated himself on the table, his feet on the bench beside Amelia.



He gave the signal to Spruce and Whimper, and they stepped away from the entrance to Cell Block W.



All in all, there were twelve cell blocks with leaders.  That meant that there were eleven leaders with eleven lieutenants arriving.  Acidbath, Galvanate, Teacher, Lab Rat and Gavel were leaders of the cell blocks on the men's side of the prison.  Lustrum, Black Kaze, Glaistig Uaine, String Theory, Crane and Ingenue were the female leaders.  There were other cell blocks, but twelve was generally agreed on as a good number.  It left room for discussion without too much chaos, and it left enough cell blocks leaderless that they had elbow room to do business elsewhere.



``This is the healer?'' Gavel asked.



``Amelia, yes.''



``My people say you're taunting them, Marquis, having this girl staying in the men's wing without a lover.''



``Not my intention, I assure you.  I would guess \emph{some people} are only looking for something to complain about.''  Marquis looked pointedly at Gavel as he replied.



``Don't waste my time with this male posturing,'' Lustrum cut in.  ``I have women to look after.  I delivered your daughter to you because you promised repayment and because she \emph{asked}.  I wouldn't mind seeing that payment.''



``It was implied that I would pay you back in coming weeks or months, not in \emph{a} week.''



``And if I ask a month or two from now, will you postpone the payment yet again?''



``I don't expect I will, but maybe you could clarify the payment you're looking for?''



``She's a healer.  Some healing would serve.''



\emph{Damn}, Marquis thought.  \emph{She had to ask}.



``Amelia isn't healing anyone right now,'' Marquis said.



``Ambiguous,'' Crane's voice was sonorous, smooth, ``Is that because she \emph{can't} or because you're ransoming her ability?''



Marquis only smiled.



``You explicitly let us know you were open for a meeting,'' Teacher said.  He didn't look like a cape in the least.  He was fat, for one thing, and he was ugly, with a red face and balding pate.  ``Don't be coy.''



``Coy?  No, let's say we're simply weighing our options and getting a lay of the land.  Healing's rare.  More than one person picked up on the fact that her codename meant `universal cure'.''



Teacher smiled, smug.



``But there's a great deal of demand, and you'll have to forgive me for being a doting father, but I won't exhaust my daughter's mental or physical resources to parcel out her healing.  We'll hear terms, we'll discuss the offers and counteroffers over the next several days or weeks, and then we'll let you know our decision.''



``You \emph{are} holding her power for ransom,'' Lustrum spoke.



\emph{A power she isn't willing to use, one that I don't know the particulars of.  Worse, it's tied to a deeper trauma that somehow involves the loss of a sister}, \emph{and that's not something that can be addressed in a matter of weeks.}



``I suppose I am,'' he replied.



Glaistig Uaine shifted position, and Marquis wasn't the only one to give her his full attention.  What he could see of her beneath the blackened tatters of her prison-sweats-turned-shroud suggested she was barely a teenager, but that was more due to her power than anything.  She'd been one of the first prisoners of the Birdcage, and he suspected she would be one well after he'd died.  Not that her megalomanical delusion was \emph{true}.  Rather, it was the fact that nobody dared to pick a fight with her.



When Glaistig Uaine spoke, her voice was eerie, a broken ensemble of a dozen people speaking in sync.  ``\emph{Beware, Marquis.  You will pay a thousandfold times for your arrogance when the armies of the faerie rouse and gather for the last war.}``



``Rest assured, Glaistig Uaine, you're scary enough on your own,'' Marquis replied, smiling,  ``I don't need a whole army of your kind chasing me down.''



``\emph{There will be no chasing, for they are already in position to strike you down the moment they wake, three hundred years hence.  You're nothing more than the dream of the faerie.  I can see it, so vivacious, so creative in its movements, even in slumber.  I think it might have been an artist.  I want it for my collection.}``



He was glad Amelia didn't challenge the `three hundred years' thing and the notion that they would still be alive then.  The `faerie' didn't react kindly to such.



``You've said as much before, noble Faerie,'' he said, ``Rest assured, you can have me when I'm dead.  In the meantime, I will keep your warning well in mind.''



``\emph{Your daughter, too.  Your faerie is kin to the one that sleeps inside the girl.  I have no doubt this Amelia is a healer, but that's only a facet of her true strength.  I have decided I will not bargain with you, Marquis.}``



Marquis used his hands to prop himself up as he leaned back.  ``A shame, but understandable.  You don't need healing, and your people are a secondary concern.''



``\emph{I will collect them as they fall.  But you are mistaken, Marquis.  I am not expressing disinterest in her talents.  I am saying that I will only deal with her as an equal.}``



In years of using his power, of breaking his own bones and feeling the pain each time, Marquis had made himself a master at hiding his emotions beneath a mask.  Even so, he only barely managed to contain his surprise.



``Very well,'' he said.  He reached into his pocket and deftly retrieved a cigarette.  He took his time lighting it.  ``We'll be in touch, then.''



``\emph{Agreed.}''  Glaistig Uaine replied.  She extended a hand to Amelia, and Marquis tensed.



\emph{Do I stop her?}



Every rational part of his psyche told him that the leader of cell block C had no quarrel with his daughter, that she was in no danger.  Every other part of him was telling him to stop her.



Amelia took Glaistig Uaine's hand in her own, then hesitated.  After a moment, she curtseyed.



\emph{I taught her to do that more than a decade ago}.



Glaistig Uaine returned the curtsey, then turned to leave.



The gathered cell block leaders watched as the self-professed faerie left.



There were capes who were deluded enough to think that their powers were actually magic.  There were capes who were neurotic in a way that \emph{didn't} shut them down or leave them unable to function.  Glaistig Uaine was one who fit both categories, and she was powerful enough to make people listen to her.  He'd never thought he could benefit from it.



\emph{Her lunacy actually plays out in my favor}, Marquis thought to himself, even as his heart pounded in his chest.  He'd planned to let the tension ratchet up until Amelia was forced to use her power to rescue him.  Applying pressure, after a fashion, without being the one to force it.  He didn't like it, but he needed her to break out of this state she was in, \emph{she }needed to break out of it for her own sake, and he was willing to risk everything to see it happen.



``It seems that cell block C will be cooperating with us,'' Marquis said.  Then he smiled.



``Glaistig Uaine might see things, but she isn't usually \emph{wrong},'' Galvanate said.  ``She says the kid has power?  Fine.  Our issues are the usual.  The dentist in cell block T charges a small fortune, and we've got some toothaches.  Can you heal that?''



Amelia was still staring off towards the entrance to Marquis' cell block.



``Amelia,'' Marquis prodded her.



``What?''  She stirred.



``Could you heal a toothache?''



``Theoretically,'' she said.



\emph{Good,} Marquis thought.\emph{  Vague, but true.}



``You're cutting into my lieutenant's business,'' Teacher said.  ``I won't take that well.''



``Competition is the best thing in the long run,'' Marquis replied.  ``But maybe we can extend you a discount for your troubles?''



``Um,'' Amelia spoke up.  All eyes turned her way.  ``A silly question, but if my dad says it's okay, maybe we can offer a deal, in exchange for an answer?''



Marquis suppressed the urge to frown.  ``I think we could.''



``I know the answer's no, but nobody really talks about it outside, so I'm not sure \emph{why}\ldots but with everyone we've got in here, why can't we break out?''



Marquis sighed.  It was a newbie mistake, to dwell on the idea of escaping, but he hadn't had the opportunity to counsel her.  It was good that she was more animated, expressing interest in something other than regret, but this wasn't helping their image and it wasn't good to let people know her full capabilities just yet.



``It's a hollowed out mountain,'' Lab Rat said.  ``Vacuum, containment foam-``



``No,'' Teacher cut him off.  ``You want the \emph{real} answer, healer?  It'll cost.''



Amelia nodded.  Marquis suppressed yet another urge to cringe.



``Measuring devices are scarce down here, so we don't have the full picture, but there's a solid running theory on why we can't just teleport out or fly through the vacuum and punch our way through the side of the mountain.''



``Do tell,'' Marquis said.  \emph{It doesn't matter in the end, but this is the first I've heard of it}.



``Size warping technology.  The device might be no bigger than a football, and that's hidden somewhere in the middle of the rocky mountains.  The warping apparatus would be bigger, but there's nothing saying it's anywhere close to the actual prison.  Reason we can't break out is because we're in a prison no bigger than your fist.  And if all of this is only \emph{this small},'' Teacher held up a fist, then tapped it against the nearest table, ``How far are you going to have to dig or teleport to get through a surface this thick?  Or through something as thick as that wall over there?  Or a hundred feet of lead with gallons of containment foam on the outside?''



``Okay,'' Amelia said.  ``I understand.  Thank you.''



\emph{That could have gone worse}, Marquis thought\emph{.}\emph{It's depressing, but it could be worse}.



Teacher shrugged.  ``Thank me with healing for my cell block.''



``A discount,'' Marquis said.



Teacher nodded.  ``A discount is possible.  What are you wanting?''



With that, the discussion was underway once more, and Marquis set about subtly setting the other cell block leaders against one another, controlling the conversation while making no promises.



This, he could handle.  He felt a quiet relief replace his fear.



\blacksquare



``Faeries,'' Amelia muttered.  They were venturing toward the communal dining area.



``Not real,'' Marquis answered her.  ``She sees things we can't, the auroras that surround those with powers.  She's named them as something else.''



``No,'' Amelia replied.  ``I saw her physiology when I touched her.  I couldn't see what she sees, but I see how she's carrying them inside her, drawing an energy from them.  And there were three more, just beside her, and she was using that energy to feed them\ldots but they weren't active?''



``She collects souls of dead and dying parahumans,'' Marquis replied.  ``Or the souls of any living soul that gets on her bad side.  But they're not souls, really.  Teacher says they're psychic images, photocopies of a single individual's personality, memories and powers.  She can have a handful active and doing what she wants walking around at any given time.''



``They're not faeries.  Or souls, or psychic images.  Our powers aren't part of our bodies, exactly.  I would be able to alter them or take them away if they were.  What I saw when I touched glass-``



``Glaistig Uaine.''



``Her.  I feel like I just got clued into a missing piece of the puzzle.  They're sentient.  Maybe they're sleeping, like she said.  But they're not dumb, and I think I'm getting an idea of what happens when they wake up.''



``Is it something we can use?''



``Not here.  Not in the Birdcage.''



``What a shame.''



``God,'' Amelia muttered.  ``Why did I ask to come here?  If I'd realized sooner-``



``Why \emph{did} you ask to come here?''



The words hit her like a physical blow.  She hugged her arms close to her body, and her hair fell down around her face.  ``My sister.  I used my power on her.  \emph{Unmade} her.''



``I'm sorry.  A result of sibling rivalry?  A fight?''



``Love,'' Amelia's voice was small.  Her shoulders hunched forward.  He took her by the hand and led her to an alcove, where far fewer people would be able to see her if she cried.



``Alas, love.  The cruelest emotion of them all.  I'm sorry.''



Marquis considered hugging her, but he didn't.  Part of it was the way she'd shied at his touch before.  He would let her approach him in her own way.  Another part of it, a small part of it, was the notion that Glaistig Uaine seemed to consider the girl to be at her level.



It was a long time before she spoke.  ``You said, before, that family was the most important thing.''



``Something like that.''



``I\ldots would you understand if I said I didn't consider you family?  I- I'm glad you're here, I'm glad to talk to you, but \emph{Victoria} was my family.''



``I understand, yes.''  Expertise let him mask the pain her words caused him.  \emph{I abandoned you to them because I was too proud to stop being the Marquis of Brockton Bay.  I should understand that you grew more attached to them than to me, yet I can't}.



``I feel like I have to do something.  This feels important.  If I could explain, tell someone who understands\ldots''



``There's no escape, I'm afraid.''



``And,'' Amelia blinked tears out of her eyes, ``Already, I feel like I'm betraying Victoria, that I'm already forgetting her.  For just a few minutes, thinking about what I just found out from that girl, I stopped thinking about Victoria.  It's my fault she isn't there anymore, that there's only that \emph{thing }I created.  If I stop thinking about her, if I stop hurting, then I feel like I'm \emph{wronging} her.''



``I suspect the pain won't stop or heal as quickly as you're thinking it will.  It hasn't been that long, after all.''



``Except\ldots if it stops at all?  If I ever forget, then I've subtracted something from the big picture.  It's not that she was perfect, but\ldots''



``But you need to maintain the memory.  Come.''



He gripped her hand and pulled her behind him.  She was too busy wiping tears from her eyes and snot from her upper lip to protest.



Still, he was glad that her face was mostly clear by the time they reached their destination.  A tinker sat at the corner of the dining area with tools strewn around him.  Makeshift devices crafted from the raw materials of their surroundings.



``How much for a tattoo?'' Marquis asked, ``For her?''



Amelia stared at him.



``Five books and five fags,'' the tinker replied.



``Old books or new?''



``Either.''



Marquis turned to his daughter.  ``If you decide to get it, I would advise a symbol rather than a face.  He won't get the description exactly right, and the image will distort your mental picture.''



``I couldn't remember her face as it was when it counted, anyways,'' Amelia said, a dark look crossing her face.



``You'll have the memory of your sister in physical form, so you can never forget as long as you live.  And when you're done, we'll take you back to your cell.  You can talk to the empty room, say what you need to say, and Dragon's surveillance will catch it.''



``It's like praying,'' Amelia said.



``Except there's a chance someone will listen and act on it,'' Marquis replied.



Amelia nodded and sat down on the bench, then she began explaining what she wanted to the tattoo artist.



\blacksquare



The house program that monitored the Birdcage followed the girl as she parted from her father and entered her cell in Cell Block W.



When she spoke, she addressed Dragon.  The program began transcribing the message as it did every word said within the Baumann Parahuman Containment Center.



Tracking programs then began reviewing the message.  Flags were raised as key words came up with some frequency, descriptions were run against a corpus of records in parahuman studies and more flags were tripped.



Sixty-two miles above the surface of the Earth, the Simurgh changed the course of her flight.



Following protocol for when Dragon was deployed on a mission, the system routed the message to one of Dragon's satellite systems.  The resulting message was scrambled by the dense signature of the Endbringer en route to Dragon.



Receiving the garbled transmission from the satellite, a subsystem of the Dragon A.I. proceeded to sort it.  A scan of the message by a further subroutine saw it classified as non-pertinent, and a snarl in the code from Defiant's improvised adjustments to her programming saw the message skip past several additional safeties and subroutines.  The message was compartmentalized alongside other notes and data that included flares of atmospheric radiation and stray signals from the planet below; background noise at best.



Considering its job done, the house program archived the transcription among fifteen years of conversation and notes from the Baumann Parahuman Containment Center.



The Simurgh flew on.





