





The crush of bodies was a tide that Tattletale and I had to push through.  There were a thousand or more scared people in our immediate area, surging against and around us.  Even our costumes didn't give people much pause or reason to give us space.  Thoughtless in their panic, the crowd was guided only by the barricades of policemen and police cars that had been established at the intersections to guide the masses to the shelters.



Everybody had been informed, in the pamphlets that came in the mail and in schools, about emergency procedures.  There were multi-level shelters spaced around the city, enough for people to hunker down in for a few hours.  They'd all been told that they could bring our larger pets if the animals could be trusted to behave.  They could bring only necessary medical supplies and what they could have on their person.  People weren't allowed to use their cars, unless they were in one of the areas on the periphery of town.  Too easy for there to be an accident in the panic and hurry, leaving everyone else stuck in a traffic jam when disaster arrived.



But people were stupid.  A chronic condition of our society, that so many people somehow thought they were special, the exception to the rule.  In this panicked crowd, every rule was being broken.  There were people with luggage on wheels, one kid carrying a lizard in a glass cage.  People were pushing and shoving, shouting and swearing.  Pets were reacting to the ambient stress with barks and snarls, dashing around and getting others tripped or tangled up in leashes.  Tattletale and I passed two cars that were even making their way forward in the midst of stampede, inch by inch, honking their horns the entire time.  Between the air raid sirens and the honking horns, I couldn't make out the words people were shouting.  I could barely think.



We reached a trio of police officers, who had used their cars and yellow tape to cordon off two sides of an intersection.  I could see the eyes on the officer nearest me widen in recognition.  He was about to say something, but the officer next to him put a hand on his shoulder, reached in the window of the police car.  He pushed pieces of paper into each of our hands.



I glanced over it, found what I needed, and gave him a curt nod.  Tattletale grabbed my hand and pulled me away.



The paper, labelled at the top with the words `Parahuman Response', contained a picture of our destination in black and white and directions on how to get there.  It wasn't far – the area which divided the Docks and Downtown, a short distance East from the mall where Brian and I had gone.



The closer we got to our destination, the more the crowd thinned out.  We saw another crowd moving toward a different shelter as we got close, but we could avoid that by detouring around that particular set of streets.



As we got close enough for me to wonder what direction to take, I saw the streak of smoke as an huge armored suit plunged down from the sky, just a block away.  It was clue enough for Tattletale to pull me forward to follow it.  Reaching the end of the street, we saw our destination on the other side of a nearly empty four lane road.



The building was fairly nondescript.  Six stories tall, it featured dark brown brick and dark tinted windows, and sat alone on a grassy hill.  A nearly empty parking lot sat between us and the building, and a stretch of beach sat on the far end.  People in PRT uniforms stood guard around the parking lot and entrance, and four of the five vehicles in the parking lot were PRT vans, with turret-mounted hoses and armored exteriors.  As good an indication as any that this was the meeting place.



Past the hill and to the left was Dragon, in a mechanical suit that was as large as two PRT vans put together, four legged, with what looked like a single jet engine on top, still smoking from her recent flight.  On either side of the engine or oversized jetpack or whatever it was, were two shoulder mounted missile launchers, each pre-loaded with four missiles longer than I was tall.  She was facing the water, unmoving, like a gargoyle standing guard.



I saw what she was watching.  A stormcloud in the distance.  It hung over the water with an opaque curtain of rain descending down from it.  It was gradually getting closer.



As we approached the parking lot, a squad of PRT officers blocked our way.  I felt a moment's trepidation.  Were any of these the same people we'd attacked at the Protectorate's fundraiser?  I couldn't tell, with their helmets and tinted faceguards covering their faces.



With a sound like a muffled thunderclap, a half dozen people appeared in the center of the empty lot.  When I saw who they were, I was awestruck.  That wasn't hyperbole or whatever, I was using the word awestruck in the original, zero-embellishment sense of the word.



Alexandria stood at the head of the crowd that had just arrived.  Her head turned from one side to the other as she surveyed her new surroundings, the long, straight black hair that spilled from the back of her helmet sweeping from one side to the other.  She was everything that made you think `superheroine'; athletic, tall, muscular, but still feminine.  Her costume was black and light gray, with an image of a tower in the center of her chest, and she featured a wide, heavy cape that flowed over her shoulders and draped onto the ground beside and behind her.  \emph{Alexandria.  }



Her team – people I recognized but couldn't necessarily name – followed behind her in a loose formation.  Only one man in a blue and black uniform and cap stayed behind in the middle of the parking lot.  He looked around for a few moments, then disappeared with a crack and a whoosh, smaller than the one that had brought the entire group there.



Tattletale and I circled around the parking lot, to avoid getting in the way of any incoming teleporters.  We were nearly to the door when we heard another group arrive behind us, the same way Alexandria had come.  Teenagers, this time.  I couldn't place them, but the brighter colors of their costumes led me to suspect they were heroes.  The man who'd teleported them in said something I couldn't make out over the the wailing air raid sirens, and they quickly set to marching in our direction.



Leading them out of the parking lot was a shirtless, muscled boy with metal skin, eyes and hair and a strange texture to his shoulders and spine.  Among other things, I noticed the tines of a fork sticking out near his neck, and what might have been the wires of a chain link fence half melted into his opposite shoulder.  But where that strange half-melted-metal texture didn't cover him, his metal body was exceedingly detailed and refined.  His `skin' was a dusky dark gray metal with the slightest of swirls of lighter metals in it, and his `adonis' musculature was perfectly etched out in the metal, with silver lines tracing his muscle definition like veins of metal in raw ore.  His eyes, too, were silver, and two lines ran from the corners of them down his cheekbones and to the sides of his jaw.



He clapped one heavy hand down on my shoulder as he passed me and offered me a tight smile.



It seemed we were allies, at least for the time being.



Tattletale and I followed his group into the building.



Folding chairs had been set into rows and columns in the center of the lobby, facing a trio of widescreen television sets, which in turn were backed by a series of large windows overlooking the beach.  Through the windows, we had the perfect view of the looming storm.



As daunting as the approaching clouds were, what drew my attention was the crowd.  There were people filling the lobby.  Only a few were local.



Empire Eighty-Eight was here, at the back corner of the room.  I saw Hookwolf there, half covered in a layer of his metal hooks and barbs.  I didn't see Cricket or Stormtiger.  He glared at Tattletale and I.



The Travelers were all present, I noted, the only other local team of villains to show.  Faultline's crew was absent, and I couldn't help but note that Coil wasn't around.  He wasn't a front lines kind of guy, but he'd at least supplied his soldiers for the ABB situation.



The local heroes were present in force.  I wasn't surprised – skipping this fight, as a hero, let alone a team of heroes, would be unforgivable to the public.  Aegis was talking with the metal skinned boy who'd arrived at the same time as Tattletale and I.  A large group of fifteen or so other teenagers were gathered and talking amongst themselves.  There was some joking, the occasional laughter, but it felt forced, strained.  False bravado.  I was assuming they were all Wards, from at least three different cities.



The kids from New Wave were near the Wards -Glory Girl, Panacea, Laserdream and Shielder- but they weren't really joining in with the conversation the Wards were having.  I could see Glory Girl and Gallant standing together; she was holding his hand.  Panacea was sitting backwards on a chair just beside where Glory Girl stood, her arms folded over the chair back, chin resting on her wrists.  She glared at the two of us, though the look was mainly directed at Tattletale.  Near Panacea, the adults of New Wave had pulled the folding chairs into a rough circle so they could sit while they talked in a bit of a huddle.



The Protectorate was present, and it wasn't just the locals, but the big guns.  Armsmaster, standing a little taller and looking more confident than I'd seen before, with not one but \emph{two} Halberds connected to his back, was having a quiet conversation with Miss Militia and Legend.  It took me a second to absorb that picture.  That was the head of the Protectorate, the leader of the largest team of capes in the world.  What's more, he was right in front of me, having a conversation with someone I'd talked to.  Ridiculous as that sounded, it affected me.



Legend sported a skintight blue costume with a design in white that fell somewhere between flame and electricity in style.  He had a perfect physique – one I didn't mind giving a second glance-over – a strong jaw and wavy brown hair.  If Alexandria was the flying bruiser that just about every other flying bruiser strove to match up to, then Legend was at the head of the pack when it came to being flying artillery.  His firepower was on par with Purity's, if not outright surpassing her, and he was far, far more versatile.



Knowing I'd seen two members of the leading three figures of the Protectorate, I looked for the third.  I glanced past Myrddin, from Chicago, with his brown burlap robe and wooden staff, Chevalier, in gleaming silver and gold armor, carrying his cannonblade, and Bastion, who had earned a great deal of bad press, lately. Someone used a cell phone to catch Bastion using the word `spic' several times as he yelled at a kid who only wanted to take his picture.  He was studiously ignoring Kaiser, who was standing nearby, staring at him, taunting him without speaking or doing anything.



It was only at the back corner of the room that I found the third member of the Protectorate's triumvirate.



Eidolon stood behind one of the large television sets, staring out the window.  He wore a blue-green skintight suit that expanded into a voluminous hood, cape and sleeves that draped over his hands.  The interior of the hood and sleeves wasn't shadowy, but illuminated with a soft green light.



Debating the relative strengths of various capes was common enough, in the schoolyard and elsewhere.  If Alexandria and Legend fought, who would win?  Would Boston's Protectorate win against Brockton Bay's team?  What if you removed Boston's weakest members until the sides were even in number?



When the question inevitably got to who was the strongest, the `big five' were generally ruled out, in the sense of `well, yeah, but besides \emph{them}`.  Scion got counted as a part of that group because the powers he did have were head and shoulders above just about everyone else's.  Eidolon was almost the opposite, because he had \emph{every power}, though he could only hold on to a handful at a time.  Then there were the Endbringers, because they mandated situations like this, where even Scion or Eidolon plus multiple teams of capes weren't necessarily enough.



Sure, some loyal people might argue that Legend was better than Eidolon, or maybe even some other cape like Dragon or Alexandria.  Generally speaking, though?  Eidolon was a top dog.



I looked away from Eidolon, to check out the rest of the crowd.  There were a few other unofficial teams of heroes, including Haven, the Christian team from the bible belt, and two teams with corporate sponsorship that were being very careful to not interact with one another.  Some sort of bitter rivalry, there.



A scattered few independent heroes and villains were around as well.  Few I could name.  I saw a girl dressed up like an old fashioned doll.  Parian.  She was local, and she wasn't hero \emph{or} villain.  A rogue, who only used her powers for business or entertainment.  She could sometimes be seen doing some promotion for a store downtown, giving life to some massive stuffed animal or a store mascot.  She'd done an interview in a magazine I'd read back before I had powers, and I knew she was a fashion student, though she wasn't revealing just who she was until after she was more established.  She looked as though she were trapped in a conversation with a curly haired, dimple-cheeked villainess that looked no older than eight, who wore a frock that was maybe from the same period as Parian's.  The pseudo-child was Bambina, if I was remembering right.



Parian was rescued by one of the out-of-town Wards, a girl in a skintight costume with a visor covering her eyes, nose and ears, with a quiver of what looked like giant needles and a massive crossbow.  The Ward said something to Bambina, who scowled and managed to look cute while doing it.  Then the heroine ushered Parian over to where she'd been talking with Shadow Stalker.  What in the world could that group talk about?  I might not have been alone in thinking that – Shadow Stalker seemed unimpressed with the new addition to their group, judging by her body language.



Tattletale spotted the Undersiders before I did.  I'd been looking for Bitch and the dogs as things that would stand out in the crowd, but they weren't present.  Tattletale squeezed my hand and gave me an apologetic smile before letting go, patting me on the upper arm, and crossing the room to head over to where Grue and Regent sat.



The two boys glanced my way, then turned their attention to Tattletale.  Ignoring me.



That\ldots really stung.



It was sort of inane, that I was concerned over something like that, given the seriousness of the present situation.  We were here because we faced the very real possibility of facing down one of the \emph{Endbringers}.  I shouldn't be worried about broken friendships.



But I was worried about it, stupidly.  I felt like I was back in school, the only kid left when everyone else had found their groups, and a hit to my confidence was not what I needed on a day like this.  I looked for a place to sit, and settled for a chair in the overall vicinity of the Undersiders and the Travelers.



Sundancer glanced at me, noted my presence, then she seemed to go out of her way to avoid looking at me again.  That caught me off guard, because I'd somehow let myself believe I'd left our cooperative battle against Lung with a good impression.  It seemed she wasn't so willing to look past the fact that I'd carved out Lung's eyes.



Feeling more and more like an outsider, more out of place, I watched as others filed into the room.  More of the Protectorate, and a small few members of the Guild.  Narwhal turned heads as she entered the lobby.  She stood seven feet tall, with a curtain of glossy, pale hair extending almost to the backs of her knees.  She was unclothed, not even wearing a skintight costume on her long limbed body, but it somehow wasn't obscene.  Her skin was layered with fine crystal scales that caught the light and scintillated with faint rainbow hues.  A single horn stood out from the middle of her forehead, three feet long.  She ignored stares as she found a space to lean against a wall near the front of the room.  She had her chin against her chest with her eyes closed, as though she were resting, or concentrating.  Or maybe it was a habit she'd picked up when standing straight meant stabbing the average ceiling with her horn.



Yet more were continuing to arrive when Armsmaster and Legend turned away from their conversation and walked up to the front of the room.  The din in the room quieted, and every set of eyes was on them.



Legend cleared his throat.  He had the kind of voice that you \emph{listened to, }``We owe thanks to Dragon and Armsmaster for their early alert.  We've had time to gather, and that means we have just a few more minutes to prepare and brief for Leviathan's arrival, instead of jumping straight into the fray as we arrive.  With this advantage, some luck, teamwork and hard effort from everyone, I hold out hope that this could be one of the good days.''



A pre-battle speech from \emph{Legend}.  It almost made the lousiest, most painful and dangerous situations I'd put up with since putting on my costume worth it.



``But you should know your chances going in.  Given the statistics from our previous encounters with this beast, a `good day' still means that one in four of the people in this room will probably be dead before this day is done.''



Or not.





