





There was a quiet murmur through the room at Legend's words.  One in four dead.  And that didn't mean the rest of us would get away unscathed.



``I'm telling you your chances now because you deserve to know, and we so rarely get the chance to inform those individuals brave enough to step up and fight these monsters.  The primary message I want to convey, even more than briefing you on the particulars of his abilities, organizing formations and battle plans, is that I do \emph{not} want you to underestimate Leviathan.  I have seen too many good heroes,'' he paused for a fraction of a second, ``And villains, too, die because they let their guard down.''



Legend paused, glanced out the window.  The storm clouds had reached the beach, and torrential rain stirred the water into a froth.  Not just rain, but \emph{buckets }of water.



``We think of Leviathan as the middle child; he was the second of the three to arrive.    He is not the physical powerhouse Behemoth is, nor the cunning manipulator that the Simurgh so often proves to be.  That said, I would advise you to think of him as having many of the strengths of both siblings at once.  You've seen the videos on television and the internet.  You know what he is physically capable of.  I want to be clear that despite the image he might convey, he is not stupid, and he can display a level of cunning and tactics that can and \emph{will} catch you off guard.''



``I will tell you what you \emph{may not know} from the videos.  He feels pain, he does bleed, but few attacks seem to penetrate deep enough past the surface to seriously harm him.  He is like the other two Endbringers in this respect.''



``What sets him apart is his focus on \emph{water}.  You're likely aware of his afterimage, his water echo.  This is no mere splash of water.  At the speeds Leviathan can move, surface tension and compressibility make water harder than concrete.  He also has a crude hydrokinesis, the ability to manipulate water, and there \emph{will} be water on the battlefield.  We believe that this is what lets him move as fast as he does when he is swimming.  Faster than he is normally, far faster than any speedster we have on record.''



He went on, ``Were it just that, this fight might still warrant a show of force like what we've gathered here.  But things are more serious than that, which brings me to our primary concern.  As much as Dragon and Armsmaster's advance warning might give us the opportunity to make this a \emph{good} day, other issues threaten to make it just the opposite.''



``I spoke of Leviathan as a hydrokinetic.  I can't state this enough – Leviathan is primarily a hydrokinetic on a \emph{macro} scale.  There is no better illustration than the days where Leviathan \emph{won}.''



``Newfoundland,'' he spoke.



I knew exactly what he was speaking of, and mouthed the date as he spoke it, ``May ninth, 2005.  Nearly half a million dead.  The Canadian island simply \emph{gone}, after the shelf of land holding it up cracked in the face of what we now understand were incredible pressures beneath the water level.''



``Kyushu, the night of November second and the morning of the third, 1999.  His sixth appearance.  Nine and a half million killed when the region was swamped with tidal waves from every direction while Leviathan disrupted prearranged evacuation attempts.  Nearly three million evacuees rendered homeless, a nation sundered.''



``These were errors, grave mistakes from defending heroes.  We had but one strategy at the time – to hem him in, minimizing the effects of growing waves and casualties until Leviathan was beaten into a retreat or Scion arrived.  These areas, however, were too vulnerable.  Waiting let Leviathan build up the strength of his attacks, and we lost.''



He paused.  ``We have since classified the locations the Endbringers target as either hard targets or soft targets.  The hard battlefields are where we stand our ground, buy time, wear him down.  The soft ones are locations where we cannot afford to do this.''



The television screen showed a cross section of Brockton Bay as seen from ground level.  The West end of the city was bordered by hills, and the terrain sloped gradually from the base of the mountain down to the water.  Directly below the image of the buildings that marked the city's location, there was a large cavern, bordered by rock on all sides except the part nearest the beach, which was sand.  It was marked blue – filled with water.



``Brockton Bay, \emph{this location}, is a soft target.  The city was originally founded at this location because of the proximity to the coastline for trade routes and an aquifier that provided the first settlers with access to fresh water.  This aquifier, essentially an underground lake beneath the city, is our weak point.  From the moment Leviathan shows himself, we expect Leviathan will stir and manipulate this underground reservoir to erode the surrounding sand, silt and rock.  Add the tidal waves from above, with the resulting tremors and impacts\ldots''



I doubted anyone failed to understand what would follow.  A section of the city, perhaps most of the city, could collapse into the aquifier.



He paused, ``We have to end this \emph{fast}.  Each wave he brings on top of us is stronger than the last.  This means we have two priorities.  First, we cannot let him out of our sight.  From the moment the battle is initiated, we hem him in, sustain an offensive onslaught.  If we let him slip past our defensive lines, precious time will be wasted chasing him, getting him in another situation where we can contain his movements.''



``Our second priority is that we need to find ways to \emph{hurt} him.  If you cannot, if your attacks are deflected or prove otherwise useless, work to support those who \emph{can}.  It is vain to hope to kill him, but he can be whittled down enough that he will flee back to the ocean, and if we hurt him enough, it may delay the time before he is capable of making another attack elsewhere.''



Legend frowned.  The windows were rattling with the force of the rain against them.  It was almost impossible to see through them with the water that streamed down, and the overall gloom beyond.



``\emph{This} is what the Endbringers are.  As of yet, we've been unable to stop them, unable to get through even one confrontation without grievous losses, be it civilian casualties, the loss of a city, or the loss of the lives of some of the bravest and strongest of us.  And they will keep coming, one after another, winning these small victories, and winning some major ones.''



``You are doing a good thing.  The greatest thing.  \emph{This} is why we are tolerated, why society allows and accounts for the capes that walk the streets and fight in its towns.  Because we are needed for situations like this.  With your assistance, we can forestall the inevitable.  Your efforts and, if you choose to make them, your sacrifices, will be remembered.''



He looked to Armsmaster.



Armsmaster spoke, authoritative, less impassioned, but confident, ``The Wards are handing out armbands of Dragon's design.  These are adjustable to slide over your arm and should be tightened around your wrist.  The screen on the top of the armband notes your position on a grid, as well as Leviathan's last updated location.  Use this.  You'll also note there are two buttons.  The button to the left lets you send messages to everyone else wearing an armband.  It will \emph{not}, unless you are a member of the Protectorate or otherwise a veteran of these fights, directly communicate what you say to everyone else wearing an armband.  Dragon has a program screening messages and passing them on through the network based on priority, to cut down on unnecessary chatter that could distract from crucial information.  If you \emph{must} bypass this three to five second delay, speak the words `Hard Override' before conveying your message.  Abuse of this feature will lose you the ability to send any further messages.''



``The second button is a ping.  Use it in the case of an emergency, to alert others if you are in danger or hurt.  If it is \emph{not} an emergency, but you want assistance, such as a flier to get you to another vantage point or you see an opportunity to turn the tables, press both buttons, tell the armband what you want.  Dragon's program will prioritize your needs, with assistance being directed your way if others are not occupied with more pressing matters.  The armband tracks your condition and will automatically send a ping if you are badly injured or unconscious.''



Legend called out, ``Capes!  If you have faced an Endbringer before, stand!''



I watched as the rest of the Protectorate, about a third of the out-of-town Wards, Bambina, half of a commercially sponsored cape team and the Travelers stood.  I couldn't help but notice Armsmaster lean over toward Miss Militia, whisper something in her ear, and point at the Travelers.  Miss Militia shook her head.



``When in doubt, follow the orders of the Protectorate first!  We have trained, organized and planned for this!  The others who are standing, now, are the ones you listen to if we aren't contradicting their order!  They have been through situations much like this, you go with their instincts!''



``We are splitting you into groups based on your abilities!  If you are confident you can take a hit from Leviathan and get up afterwards, or if you have the ability to produce expendable combatants, we need you on the front line!  You will be directed by Alexandria and Dragon!''



As a share of the crowd moved toward one corner of the room, Armsmaster stepped down from the podium to approach Tattletale, Grue and Regent, ``Where's Hellhound?''



``At least call her by her real name,'' Tattletale glared up at him, ``She's not here.  You knocked her dogs around enough to know they aren't \emph{that} tough, and that means you're implying they're expendable.  Be glad she wasn't around to hear that and figure that out.''



Armsmaster opened his mouth to respond, but broke off when Legend called out his name.



``Armsmaster and Chevalier will be leading the hand to hand combatants who do not fit in Alexandria's group!  Anyone who thinks they can harm or hamper Leviathan in close quarters, you'll be assisting and reinforcing the front line!''



Armsmaster strode away from the Undersiders, and I saw Assault, Battery, Brandish, Night and Fog move to join that group, among others.  Smaller than the first group, but I suppose it took a certain amount of bravery to be willing to get close to an Endbringer when you weren't invincible or close to it.



The boy with the metal skin began to pass through my row.  He handed me an armband from a bag, and I slid it over my hand and cinched it in place.  A flat, square screen showed a satellite view of the building we were in, and the surrounding parking lot and beach.  A display read: `State name'.



I pressed the communicator button and spoke, ``Skitter.''



My name appeared on the display, with a yes and no display in the corners over the respective buttons.  I confirmed it.



Legend was still organizing the groups.  ``--forcefields, telekinesis, whatever your power, if you can interrupt Leviathan's movements or help reduce the impacts of the waves, you're the backup defense!  Bastion will direct you!''



I was also all too aware that the size of the group that was still sitting was dwindling, and I had no place to go.



``Movers!  We need fliers, teleporters, runners!  You'll be responding to pings!  Rescue the fallen, get them to emergency care, assist any others where needed!  Myrddin will give you your orders!''



``Long ranged attackers, with me!  If you fall in more than one category, go with the group where you think you'll be the greatest assistance!''



Did I count as a long ranged attacker?  No, my power wouldn't hurt Leviathan.  I turned to look at those of us who were still seated.  I recognized Grue, Tattletale, Regent, Othala, Victor, Panacea and Kaiser.  There were a half dozen more who I'd never seen before.  People from out of town.



``The rest of you--'' Legend was interrupted by shouts.  Bastion bellowed, pointed, and the people in his team moved.



Layers of forcefields went up around the far wall in front of and behind the front windows, and they weren't enough to take the hit.  The building rocked with an impact, the forcefields to the left collapsed, and the water began to rush in, carrying chunks of brick, glass and the metal windowframes into the lobby.



One of the television screens toppled in the onrushing flood.  The other two showed a flickering series of images, a half second of each.  The coast of Brockton Bay being struck with a wave.  The ferry, the harbor down at the south end of town, the boardwalk, all smashed by the initial wave.  I saw a glimpse of a tall figure in the middle of one shot, little more than a blur behind the spray of water and the rain.



There was a loud groan, and the ceiling at one corner of the room began to descend swiftly toward the ground.  Narwhal flicked two fingers up in that direction, and shored the ceiling with some forcefields, but I saw other portions of the ceiling begin to sag, gallons of water pouring through the gaps in the ceiling tile.



``Strider!'' Legend bellowed, over the noise and chaos, ``Get us out of here!''



A voice sounding from the armband, female, synthesized, except I couldn't make it out over the noise.



The air was sucked out of my lungs, and there was a noise like thunder.  My entire body was rattled down to the core, and I thought I might have been struck by lightning.  I was outside, I realized, on my hands and knees in what I first took to be the middle of a shallow river.  The rain that pounded down on us was more like a waterfall than any rainstorm I'd been in.  The taste of the salty ocean water filled my nose and mouth.  My soaked mask clung to my lower face, forcing me to hang my head to keep my breaths from pulling more water into my mouth.  A few coughs and heavy exhalations cleared the worst of it away.



We'd arrived in the middle of a road, one I'd crossed several times when going to the loft or leaving it.  It was still dark out – either the sun either hadn't started to rise yet, or the storm was enough to obscure it.  The `river' that I was kneeling in was the ebb of water from the first tidal wave, receding downhill toward the beach and the ocean.  It brought waves of trash, litter, broken windows, wooden boards and dead plants with it.



I looked around, saw the other heroes and villains composing themselves, climbing to their feet in the knee deep rush of water.  A few fliers were conveying our ranged combatants up to the rooftops.



At the end of the road, downhill, was the Boardwalk, or what was left of it.  From what I could see through the downpour, the wooden pathways and docks had been shattered by the initial wave, to the point that many were standing nearly straight up, or were buckled into fractured arches.  Water frothed and sprayed as it rushed back against the ragged barrier that had been Brockton Bay's high end shopping district.



He was there, too.  I could see his silhouette through the rain and the spraying water that was the tidal wave's aftermath, much as I had on the television set.  Thirty feet tall, the majority of him was was muscled but not bulky.  His hunched shoulders, neck and upper torso were the exception, bearing cords of muscles that stood out like steel cables.  It gave him a top-heavy appearance, almost like an inverted teardrop with limbs and a tail.



His proportions were wrong – his calves and forearms seemed too long for his height, his clawed fingers and digitigrade feet doubly so.  He moved with a languid sort of grace as he advanced through the spraying water.  His arms moved like pendulums, claws sweeping against the water's surface, while his upper body swayed left and right, as if to give counterbalance to his great height.  His tail, forty or fifty feet long and whiplike, lashed behind and around him in time with his steps, perhaps borne of the same need for balance that gave him his teetering gait.



Gallons of water poured around him in the wake of his movements, roughly the same amount of mass as the body part that had just occupied the space.  This `afterimage' streamed down him and splashed violently against the water he waded through.



As he got closer to the heroes and villains that were organizing into lines, shouting something I somehow couldn't hear over the buzz of fear and adrenaline, I could almost make out his face.  It was something you never really saw in the videos or pictures.  He had no nose or mouth, no ears.  His face was a flat, rigid expanse of the same scaly skin that covered the rest of him, like the scales of a crocodile's back.  The hard, featureless plain of Leviathan's `face' was broken up only by four cracks or tears – one on the right side of his face, three on the left.  In each of those dark gaps, the green orbs of his eyes glowed with a light that pierced through the rain.  His head moved faster than the rest of him, twitching from one angle to the next like someone's eyeball might flicker left, right, up and down, taking us all in, uncannily out of time with the rest of his body.



``Get ready!'' Legend howled the words.



It was hard to say whether Leviathan heard the command or if Legend had spotted some tell, but Leviathan dropped to all fours at the same time Legend gave the command. With Legend's cry still ringing in the air, Leviathan \emph{moved}.



He was fast.



Fast enough that his clawed hands and feet didn't touch the road beneath the water – after the initial push, his forward momentum was enough to let him run on the water's surface.



Fast enough that before I could finish drawing in a breath, to scream or shout something or gasp in horror, he was already in the middle of us, blood and water spraying where he collided with the lines of assembled capes, and the armbands were beginning to announce the hopelessly injured and deceased.  \emph{Carapacitator down, CD-5.   Krieg down, CD-5.  WCM deceased, CD-5.  Iron Falcon down, CD-5.  Saurian down, CD-5\ldots}





