





As tough or invincible as a given cape might be, most were still hemmed in by the restrictions and boundaries of physics.  Getting hit by something that weighed nearly nine tons sent men, women, boys and girls in costume flying, if it didn't kill them outright.



Leviathan's echo added surprising quantities of water to the battlefield.  Every step and movement he made, he filled the space he'd just left with water.  How much water did it take to displace something as big as he was?  However much it was, he created something like three times that amount when he took a single step forward, when you accounted for the space his body moved through.  A hard amount to eyeball, because it had the same momentum his movements had, and some of it crossed great distances as he lunged and clawed his way through the front line of capes.



\emph{Sham down, CD-5.  Acoustic deceased, CD-5.  Harsh Mistress down, CD-5.  Resolute deceased, CD-5.  Woebegone down, CD-5\ldots}



I had to help, somehow.



I pressed both buttons on the armband and spoke into it, ``Direct me to the wounded I can help.  I do not have mobility powers.  I am \emph{not} very strong.  I \emph{do} have basic first aid training.''



There was a pause, then a female voice, synthesized, just sharp enough to be heard over the noise of lasers, guns and rain, ``Acknowledged.''



The response both relieved and terrified me.  I'd halfway expected that to fail.



My armband beeped and flashed, and I saw a red dot on the map, along with an arrow at the edge of the square screen.  As I moved my arm, the arrow adjusted to keep pointing the same way.  It was directing me to near where Leviathan was.



Lashing out with tail and claws, he was advancing steadily through the ranks of defenders.  The occasional strike from a strong hero or one of the ranged combatants slowed him, made him stumble, if it hit in the right spot or pushed him off balance.



I hesitated to get closer.  I hated myself for doing it.  I was here for a reason, to do \emph{something}.



Legend fired a salvo of lasers at Leviathan, and the beams turned at right angles to strike Leviathan in precise areas, knocking his feet from under him, slamming him down into the road, catching him under the chin.  Leviathan raised a hand, and a geyser of water rose to block more incoming lasers.  Legend's lasers simply turned at angles to circle around Leviathan, strike the Endbringer from behind.  They left Leviathan so hot that his flesh glowed a yellow-orange around the areas they struck him.



I took the opportunity, found some measure of courage and hurried forward to my target.



There was a leg, half floating, weighed down on one end by a metal boot on the foot.  Someone in a leather costume lay on their back, barely conscious, bleeding from a gash that had opened them from the left hip to their right shoulder, a cloud of blood spilling out in the filthy water that came halfway up to our knees, an inky black color in the gloom.



I couldn't help them, as much as it pained me to ignore them, move on.  I had to trust that the armband would direct me to someone I \emph{could} help.



I found the person my armband was directing me to, some teenage boy with a metallic bird design to his costume, the helmet that covered the upper half of his face looked like a bird's head, maybe an eagle.  I knelt by him.



There was a crash as Leviathan whipped his tail toward Legend, a blade of water soaring through the air to strike the hero out of the air.  The onslaught of lasers interrupted, Leviathan shifted from a crouch on one side of the road to being the midst of the defending heroes in one fluid motion, resuming the carnage in the span of a heartbeat.



\emph{Fierceling deceased, CD-5.  Adamant down, CD-5}



He was way too close to me for comfort – a single leap on his part would close the distance to me – but freaking out over it wouldn't help anyone.  I could only hope that the front line would hold for long enough for me to help this person.



``What can I do?'' I asked the bird-costume.



``Leg,'' he said, voice strained, ``Help me stand.''



His left leg, I realized, was smashed into pulp from the knee down.  I crouched, helped him get his arm over my shoulders, and used my legs to heave both of us into a standing position.  The bird-costume was below average in weight for a teenage guy, but it wasn't exactly easy.  He \emph{was} wearing armor.



I might not have been able to get both of us up to a standing position like that if it weren't for my weeks of running.



He leaned on me heavily with each step forward, and we retreated from the front lines.  Someone with the ability to fly landed not far from me to pick up the man with the gaping wound across his torso, flew off with him.  Two seconds later, a teleporter blinked into existence near us, touching two fallen capes, and disappeared with them and a bathtub's worth of water.



I wanted to apologize for not having a better power to help this person, but the breath would have been wasted.  It was hard work to help him along, to slog through the water.



The fight was ongoing, with a dozen heroes in Leviathan's vicinity, more than twenty others shooting at him from range whenever there was a clear shot.  Yet more were on the fringes, to keep him from slipping past the combatants and to take the place of the fallen.  It wasn't enough – the damage we were doing was negligible and his long strides were advancing him further and faster than the rest of us could back away through the water.  Trash and debris threatened to trip us up with every step we took.  He forced a fighting retreat, moving quickly and often enough to avoid being caught by any concentrated fire.



Our progress was agonizing.  Move too slowly, and we fell behind, move too fast as we waded through the trash-ridden water, and we risked falling, lost precious time.  Had to find the middle ground, and we weren't moving fast enough even if we did find that sweet spot.  Hell, it would have been kinda difficult even without my burden.



\emph{Chubster down, CD-5. Good Neighbor deceased, CD-5.  Hallow deceased, CD-5.}



It was Alexandria who speared forward to confront Leviathan.  He saw her coming, ceased his onslaught to rear back and then lunge ahead to meet her.  When they were only fifteen feet apart, he stopped, let his water echo rush forward to meet her.



Anyone else might have been staggered in the face of several tons of water moving forward at the speed of a locomotive.  Alexandria intertwined her fingers, swung her arms forward as though she were holding a baseball bat, and cracked her hands against the image a second before she disappeared headlong into it.  There was a sound like a bomb going off, water spraying everywhere, followed by an earthshaking crash as Alexandria used the crook of her arm to catch Leviathan around the neck and heaved him backwards and onto the ground.



Most of the capes took the chance to retreat and expand the gap between themselves and the Endbringer, firing lasers or sonic blasts or whatever else at him as they retreated.



It was so strange to think I was just like the rest of these people.  Even after all this, the last few long weeks to get used to being in costume, it felt like I was the bystander.  Maybe it was that my power was ineffectual here, in the water and the rain, maybe everyone felt that way.



A flier with fringes of ribbons down the sides of her arms, legs and body landed next to me, ``Give him to me.''



We transferred the bird-boy to her grip, and they were gone in an instant.  My armband flashed and pointed me toward the next target.



A series of explosions and a massive collision marked Dragon firing a full salvo of missiles and entering close quarters combat with Leviathan.  Alexandria was gone – no, wait, she was rising from the water, where Leviathan had been holding her down.  Standing, staggering, falling again.  Had he been drowning her?



Dragon began breathing out a stream of what might have been plasma in Leviathan's face.  From his increased struggles and frenetic clawing at her, I gathered he didn't like it.  Still, it was doing surprisingly little damage to him.



Leviathan found a point to get a solid grip on Dragon's armor, and tore off a plate.  His next swipe took off another, and it careened a good twenty feet before landing with a heavy splash, close enough to me that I was caught in the spray.



I hurried to the next target on my armband.  It was a woman with a white costume, white hair and what was probably skull paint on her face.  It was hard to tell, and not just because of the rain smudging the make-up.  Nearly half her face was torn off.  Glanced by one of Leviathan's claws, maybe, or caught by the lash of water from his tail.



``Hey,'' I shook her gently by the shoulders, ``You awake?  You alert?''



Maybe a stupid question.  I didn't even know if she could talk with her face like that.



A small wave sloshed against us, she sputtered and turned her head, didn't respond.  That was a `no' to at least one of my questions.  I suspected her condition was a combination of shock and blood loss as much as anything else.



Too heavy for me to lift, and I didn't have first aid supplies.  Fuck, I could have kicked myself for that.  Anything I did have – epipens, smelling salts – were probably spoiled by the water and the septic conditions.  Not that they would have helped.



I looked up, looked around.  Spotted what I needed.  Someone was manifesting green fireballs in his hands, lobbing them at Leviathan, where they exploded violently.



I rose, hurried to him, keeping low so I didn't walk face first into anyone's laser blasts or gunfire.  ``Your fire, is it radioactive? Is it anything special, extra dangerous?''



He gave me a look, lobbed another fireball, ``It's fire, it combusts if I concentrate it.''



``Okay.  Great.  I need your help.''



He nodded.



I showed him the woman.  ``Blood loss is a problem.  She needs the wound cauterized.''



His eyes widened, ``I can't do that!  Her face-''



``-Is half scraped off.  She's not going to care about a burn.  There's nothing close to a clean bandage anywhere here, and she's going to die if we don't stop the blood loss.''



Looking a little sick, he nodded, wreathed his hand in flame and then pressed it against the woman's face.  She pulled away, made a gurgling noise.  I gripped her head and shoulder to keep her in position.



``Come,'' I said, after he pulled his hand away, ``Help me move her.''



Greenfire – I wasn't sure on his name, and it didn't seem the time to ask – hooked one arm under her armpit, I used both hands under the other one, and we hauled her off to one side, into an alley, propped her up sitting.



``I'll stay here,'' Greenfire said, ``Keep an eye on her.  You go.''



I nodded, pressed both buttons on the armband and spoke, ``Next!''



As we emerged from the alley, there was a massive explosion, five times what had followed when Dragon launched her missiles at Leviathan.  Leviathan reeled – He had a shallow burn along one side of his neck, more on his face, one of the four glowing orbs of eyes were dim, but it wasn't as much damage as I might have suspected.  He lashed his tail violently, as if in anger, or maybe he intended to use the echo of his tail's lashing to strike down others, I couldn't be sure.



It was a contingent of lesser heroes that joined the fray, now.  It was as though the tougher fighters were staggering their attacks, to ensure that just the right amount of force was being exerted to keep Leviathan on his heels, taking the maximum amount of damage while being prevented from taking out too many capes at once.  These three were clearly members of the same team, flying in formations, moving in sync.  Two of them had super strength, and were gripping at the damaged areas of Leviathan's flesh, tearing, pulling away as he lashed out in response, while the third had a massive battleaxe with what looked like a chainsaw setup on each blade, opening more wounds.  The damage was superficial, only taking off slices of Leviathan's hide, but surely stripping away his hard exterior would help in the long run?



The armband directed me to someone that was already getting assistance.  An obese cape in armor, getting CPR from a man with a princess-bride style mask over the upper half of his head, a goatee, a chainmail lined mantle and a shotgun three times the normal size.  He didn't know what he was doing – the fat man's chin was almost touching his collarbone.



When I moved to take over, Shotgun Westley left without a word, wiping his mouth and unslinging his gun as he ran back to the fray.  I was irritated.



\emph{Hew down, CD-5.}



It was my first time giving CPR for real.  So much harder than it was in the class, on so many levels.  I don't know if it was the fat man's powers, his weight, his armor, or some combination of the three, but it took incredible effort to actually fill his lungs.  Just doing it made me want to gag.  He'd vomited a little at some point, and though I'd wiped it away as best as I could when I was done checking his mouth for blockages, the taste lingered.  The taste of salt water only accented that flavor, sort of the same way table salt did with a cooked meal.



\emph{Strapping Lad down, CD-5. Intrepid down, CD-5.}



I was aware of Narwhal stepping into the fray, in my peripheral vision.  She raised her hands, manifesting a dozen forcefields like oversize crystal shards around her, then flicked them forward.  Like guillotine blades, the forcefields raced toward Leviathan, faster than the eye could follow, sunk into his flesh.  Those that glanced off stopped mid-air to turn around, edges against his body, getting in the way of his legs moving.



There was a horrendous crash, I looked up, pausing to catch my breath, saw the remains of a car falling apart around Leviathan.  Another crash, a piece of rubble turning to dust from the speed of the impact.  I couldn't see through the bodies, but I had an idea of who it was.  Ballistic.



A dumpster hit Leviathan in the upper body with the speed of a bullet, and he folded backward, his shoulders hitting the ground while his legs and feet were still held against the ground by a mess of razor blade forcefields.  Narwhal sent another forcefield flying into his neck, and it cut as deep as any attack had yet.  Blood spilled down from the opened wound, thick, more like ichor than anything I was used to seeing.



I heaved another breath of air into the lungs of the fat man, he sputtered, coughed up a mouthful of dark water.  I knew I was supposed to follow up on the CPR, but there was no way I could move or roll this guy.



Unable to do anything but wait and see if he recovered, I raised my head to watch the continuing battle, feeling just a touch dizzy.



The ranged attack continued.  Miss Militia had a bazooka as long as she was tall, and was firing a series of warheads into Leviathan.  She wasn't reloading, either.  Between shots, the weapon crackled with energy, fresh ammunition loaded into the chamber by her power.  One projectile fired off each second.



There was the girl with the crossbow, who had been with Shadow Stalker.  She had a teammate next to her, handing her the needle-like bolts from a quiver, was loading them into the large crossbow and firing them as fast as she was able.  More than any other attack, the bolts were stabbing deep into Leviathan.



The attacks were actually having an effect.  He was on the defensive, now, and he was hurting.



\emph{We're winning}, I thought.



A flash to my left caught my eye.



It was my armband.  The screen was ringed by a square of yellow, a yellow triangle with a black exclamation mark pointing in Leviathan's general direction.



People were shouting.  Screaming, Narwhal was moving forcefields up in between us and Leviathan, other forcefields were going up.



``To me!'' someone near me shouted.  I turned to look, saw Shielder from New Wave.



\emph{Tidal Wave}.



The fat man's eyes weren't even open, he moved too slowly as I shook him.



There was no helping it.



I gave the fat man one backwards glance, and bolted for Shielder. I mouthed an apology I didn't have the breath to utter, more for my conscience than for the man I hadn't saved.



Shielder waited until the last second to erect his cerulean bubble around himself.  I caught a glimpse of one cape, a step too slow, getting trapped on the outside, a half second before the wave hit.  Crushed against the exterior of the solid-light forcefield by the onrushing waters.



I'd been in an earthquake before.  A three on the Richter scale, brief.  I'd been at home, and a check of the house afterward only found a few books knocked off the shelf, a mirror fallen from the wall in the front hall.  This was a hundred times more intense, the water rolling over us, against the nearby buildings, making the ground shudder.



For one brief moment, we were submerged, currents running past Shielder's bubble.  water in front of us, to either side, behind and above.  Outside the translucent bubble, I saw a massive dark shape zip past us, saw Shielder fall to his knees, as though the force of the water against the bubble in Leviathan's wake was nearly more than he could bear.



\emph{Heavy casualties, please wait}, a chorus of identical voices announced, coming from the armbands of those ten or twelve of us in the bubble.  Telling us that we'd just taken losses so heavy that the Dragon's computer system couldn't or wouldn't list them all.



The water surging around us stopped abruptly, evaporated into a mist in a second.  Swirling, the mist began drifting.



Myrddin, working with Eidolon. They stood in the center of the road, Eidolon turning the water into mist, while Myrddin gathered it.  Myrddin's wooden stick was held aloft, and the mist was forming a sphere the size of a beachball at one end.



Ok, I could \emph{almost} buy the wizard angle, seeing that.



Leviathan leaped from the roof of a nearby building, landing in the midst of one group that was still reeling from the wave, started tearing through them.



The armbands remained ominously silent, even as I watched the casualties.



Myrddin pointed his staff and launched that orb at Leviathan.  It hit harder than anything yet, and the brute was sent flying into the interior of a nearby building.



``Seal him off!'' someone shouted.  Chevalier.  ``Make him come back our way!''



Forcefields went up around the exterior of the building.  The building itself bulged and warped as Vista exerted her power, thickened the walls, made the middle floors of the building draw together slightly, a slight hourglass shape.  I saw her, wet and worn out, one hand raised, shouting something I couldn't make out at one of the out-of-town Wards.  The Ward was speaking into his armband, replaying some message.



\emph{Depart from the rooftops, buildings may come down}\emph{imminently}, my armband announced.



Flying capes left the roof of the building, each carrying someone.  They were still leaving as Leviathan lunged through the side of the building and the forcefields that had been reinforcing the walls.  He tried to retreat, was stalled by more forcefields.  I saw a figure on the far side.  Bastion.  The hero who had been in the news over his racist tirade.



Bastion bellowed, ``Do it!''



Leviathan lunged, crashed through one barrier, making it shatter like glass, only for another to appear immediately after.  He turned to head our way, was stopped by another.



``Fucking do it!'' Bastion called out, barely audible.



The building above him bent and the midsection, unable to support the upper floors, crumbled.  The upper half of the building crashed down atop Leviathan and Bastion.



Vista turned, wrapping her arms around the Ward next to her, burying her face in his shoulder.



``Move forward!'' Armsmaster called out, ``He's going to want to escape to recover!  We can \emph{not }let him!''



Leviathan had more than halved our ranks with the wave.  I could see people face down in the water.  Others were crumped up, their bodies contorted, broken, still.



And the damage to the city was just as bad, in a different way.  I stared at the wreckage, the block and a half of shattered buildings, and saw a looming mess of arches and massive iron beams and girders, unable to comprehend what it was.



It dawned on me.  The PHQ.  The headquarters of our local superteam, tourist attraction, torn from whatever fixtures had rooted it in place, smashed to ruins against our coastline.



The Armband spoke. \emph{Losses are as follows: Debaser, Ascendant, Gallant,Zigzag, Prince of Blades, Vitiator, Humble, Halo, Whirlygig, Night, Crusader, Uglymug, Victor, Furrow, Barker, Elegance, Quark, Pelter, Snowflake, Ballistic, Mama Bear, Mister Eminent, Flashbang, Biter\ldots}



The names kept coming.  I almost wanted to cover my ears, but not knowing for sure was worse.



\emph{\ldots{}Cloister, Narwhal, Vixen, The Dart, Geomancer, Oaf, Tattletale\ldots}


The recitation continued, but I was numb to them.  Tattletale?  I started, looked around, as if I could find her.  Where had she been?



No, what I suddenly \emph{really} wanted to know was what the armband meant by losses.  Were all those people dead?  Was \emph{Tattletale} dead?  Why wasn't the armband directing me to help someone?  Was there no point, or were our numbers so reduced we couldn't afford to?



I could hope it was the latter, but having seen some of the injuries I had, it didn't make me feel better.  It was almost worse, thinking that Tattletale might by lying somewhere, bleeding out or unable to breathe, not getting help.



``Be ready!'' Armsmaster called out.



Leviathan heaved himself up out of the building's remains in one motion, used his tail to pick up and fling a mess of broken wood, concrete and rebar at us.  Aegis threw himself into the cluster of projectiles, but two capes were struck down by smaller chunks.  A third was folded in half by the arc of water from Leviathan's tail.



Brigandine deceased, CD-5.



I couldn't afford to dwell on what might have happened to Tattletale.  I wiped beads of water from the lenses of my mask with my gloved hands, pushed my hair out of my face, and made a note of my bugs.  There were scant few in the way of bugs that could navigate in this storm.  Myrddin had banished the water from the wave, somehow, but the downpour was making the streets flood fast enough that I didn't trust anything to crawl.  No, my power was dead useless, here.



Leviathan turned around, lashing his tail behind him to cast three lashes of water our way, then crouched.



``He's running!'' someone called out.



Leviathan dashed away from us, \emph{fast}, only to skid to a stop and turn a corner for cover as Legend, Lady Photon, Laserdream and a half dozen other heroes opened fire from the skies above.



Others had picked themselves up, were moving into the side streets and alleys to follow, intent on cutting him off.  I looked around, glancing over at the injured and wounded, knowing Tattletale was among them.



Eidolon was staying behind, raising his hands, and green sparks began rising from the ground, clustering around Eidolon and the fallen, obscuring them.



A second later, he and half of the bodies that had been scattered around the battlefield disappeared, the sparks blooming outward in twenty small firework explosions.



I took that as my cue to join everyone else in the pursuit.  Eidolon could help the wounded.  I couldn't, really.



I ran after the others, nearly tripping into a pothole in my hurry.  My armband showed a green icon for Leviathan, and I followed it.



Rounding a corner, I came up at the rear of a small crowd, perilously close to the Endbringer.



Fog was blocking one route, while Sundancer stood at another, her superheated orb between her and Leviathan.  The remaining capes were divided between the other two possible alleys Leviathan might have moved through and the air above him.  Legend was hammering Leviathan down to the pavement with a series of laser blasts.



``Care!'' Miss Militia cried out, ``Fire in the hole!''



She fired a shot from her grenade launcher, grabbed another grenade with a blinking LED from her vest and loaded it into her gun.  Why?  She'd shown with the bazooka that she didn't need to load ammunition, hadn't she?



Then I realized why.  It wasn't the kind of ammunition you found in normal guns.  The first shot exploded into a mess of golden sticky ribbon, familiar, though it somehow escaped my memory where I'd seen it.  The second exploded in midair, near Leviathan's shoulder, leaving the tips of the scales and one gaping wound glinting like crystal.  As Leviathan moved to recoil, the edges of the crystal separated from his flesh and seeped with that dark ichor.



The third was a modified explosive I recognized.  It bounced off the ground between Leviathan's foot and the hand he had planted on the ground, landed a ways behind and to the side of him, and exploded much like any other grenade might.  What I recognized was the shimmer in the air around it, a near perfect sphere encompassing the surrounding area, catching Leviathan's leg, the end of his tail, part of his waist and stomach.



The explosion made Leviathan rear back, and the water that followed in his wake moved slower in that bubble, slowed down with each passing second.



Leviathan himself wasn't as affected, and he had one foot and an upper body outside of the bubble to help him pull himself free.  He raised his leg free of the golden string goop and up out of the sphere, lashed his tail toward the crowd I was at the back of, catching three people, entwining the tip around their arms, legs and necks.  He flicked them into the center of the time distortion bubble, where they got caught, unable to make their exit fast enough to avoid being frozen in time.



\emph{Jotun deceased, CD-6.  Dauntless deceased, CD-6}.  \emph{Alabaster deceased, CD-6.}



He lashed his tail, sending out a scythelike blade of water toward the other group, turned and leaped.



\emph{Miss Militia down, CD-6.}



Fenja and Menja moved to attack him, each tall enough to be at his shoulder level, but Leviathan was quicker.  He darted backward, gripped the side of a building, and turned to \emph{run up the wall. } He used his tail to radically adjust the angle of his ascent, hooking it on an open window and swinging himself forward over the edge of the roof, before anyone on the ground could get a bead on him.  Debris fell where his tail had pulled through a section of the wall.



Though he'd disappeared from my line of sight, I saw his afterimage continue rising.  Shielder, floating in the air with the help of his sister, used a forcefield to stop the pair of them from being pulverized.  The shield flickered out of existence a fraction of a second later.  His reserves were exhausted, after helping save me and others from the last wave.  He wasn't strong enough to take a hit from Leviathan or his afterimage.



Legend fired a barrage of lasers at Leviathan, but the Endbringer was quick to hop to one side, landing on the roof's edge.  He made a sudden, standing leap a good eighty or a hundred feet into the air, tail extending to reach for the airborne heroes.



The whiplike tail struck Legend, and there was a firework display of light and sparks, Legend tumbling out of the sky, head over heels.  In the same movement, the tail reached for Laserdream and Shielder.



\emph{Legend down, CD-6,  }The armbands announced, just in time to coincide with Legend hitting the ground.



Laserdream put her own shield up, and I could remember how Photon Mom, Laserdream and Shielder all had the same basic powers.  The difference between them was that while Photon Mom's powers were well rounded, Shielder had a far, far, better forcefield, almost no flight ability and weak laser blasts.  Laserdream was the opposite\ldots her lasers and flight were good enough, but her forcefield, not so much.



Leviathan wrapped his tail around the spherical forcefield that surrounded the siblings, bringing it and the pair down toward the roof as he fell.  When they were halfway down, the constriction of the tail broke through the forcefield, snaked around Shielder's body and Laserdream's arm.



The Endbringer landed on the roof with a shuddering impact and a showering of detritus, crashing through the roof.  He bounded up to the edge of the roof, lunged off it.



I could see it like it was slow motion.  Laserdream's hand glowed and she fired, using the concussive force of her laser to get her trapped hand free, flew up and back out of the way as Leviathan continued to fall.



Shielder, still in Leviathan's grip, had his upper body brought down against the ragged edge of the building in passing.



\emph{Shielder deceased, CD-6}



Laserdream's ragged scream was like something distant, something I was barely aware of, because Leviathan was landing back in the area where the two alleys met.  He leaped in Sundancer's direction, caught the ground with the claws of his hands and feet to halt his momentum.  His echo surged forward, some striking the superheated orb, where it blossomed into massive clouds of steam.  The rest went low, catching Sundancer below the waist, sweeping her legs out from under her in one violent rush.  She flipped forward, her upper body colliding with the ground.  The miniature sun winked out of existence.



\emph{Sundancer down, CD-6.}



Turning on the spot, Leviathan moved his claw, creating a wave with all of the water he'd generated since entering the alley, driving it into one of the two gathered groups.  As those capes stumbled and fell back, Leviathan leaped over the time distortion bubble, landing at the front of the \emph{other }group.  The group with some of the local wards, Velocity, some of Empire Eighty-Eight, and out-of-town capes I couldn't name.



The group I was at the rear of.



Someone stepped up to grab him mid-lunge – some woman I didn't recognize, who Othala was touching.  She was granting this woman some form of invincibility that let her take a hit and not get knocked away by Leviathan.



Invincible though she might be, she couldn't do anything to stop the afterimage from crashing against and around her, through our assembled ranks.



I was shoved back – not by the water itself, but the tide of bodies that were struck, crushed and thrown by the afterimage.  As I was pushed backward, hard, I was spun by an impact at my shoulder.  My arm slammed against a windowsill, and it exploded with a sharp, jarring pain.  I landed on my back, saw someone else get sent head over heels over the crowd, colliding against the wall with an audible cracking sound, landing limp as a rag doll, a matter of feet from me.  He had a trumpet and a flag on his chest.



\emph{Escutcheon deceased, CD-6.  Herald deceased, CD-6.}



Kaiser – I hadn't even seen him in the group – erected a latticework of blades across the front of the alley, between us and Leviathan.  It wasn't enough.  Leviathan tore through them like I might tear through a wicker basket.  Edged pieces of steel spun through the air and clattered to the ground.



Kaiser changed tactics, creating columns of steel instead, each three or four feet across, harder to shatter.  They were slower to emerge, but they bent rather than broke.



Leviathan responded by \emph{pushing}. He exerted his full strength on the barrier of blades and the columns, leaning against them.  The walls broke around the base of the columns, and the pieces of steel fell.



A stab of pain from my arm reminded me I was hurt. \emph{Fuck}, it hurt a lot.  It throbbed, and each throb seemed to be worse than the last.  I felt shaky as I used my good arm to stand.



Leviathan didn't make noise.  I kept expecting a roar, or hiss, or something, but Leviathan was dead silent.  I somehow imagined a victorious howl as he broke through the barrier, crouched, and lunged into the crowd.



He stopped, and I thought he was using his afterimage, halting so it could rush forward, but even the watery echo stopped a second after it appeared, only the very edges of it continuing forward to crash violently against the sides of the alley.



For several long heartbeats, it was nearly quiet, but for the sound of rain, people's noises of pain, mine included, and the sound of one of Kaiser's iron columns ripping free of the wall and falling atop a pile of blades.



It took me a second to realize what had happened.  Leviathan hung frozen mid-pounce, and his emerging afterimage similarly stood there, frozen in time.  In the midst of the afterimage was Clockblocker, half-immersed in water.



``Someone get him out of there!  He's going to suffocate!'' I shouted, my voice made that much more edgier and strained by the pain I was in.  My voice, though, coincided with no less than five other cries, all rising to be heard over everyone else.  Trap Leviathan, contain him, use more of those grenades to get him before he got free.  Someone was even shooting arcs of lighting at Leviathan's frozen form.  Too many commands from too many people who hadn't fought with or against Clockblocker, who didn't know how his power worked, who had conflicting ideas on what we had to do.



This chaos would fuck us over, keep us from accomplishing anything before Leviathan got free.  We needed order, and most of the people who could have given it to us were out of action or nowhere nearby.



The armbands.  Armsmaster had said it prioritized orders based on need.



My left arm hung by my side, and I couldn't even bring myself to raise it.  Just gravity and the weight of my hand pulling down on it was excruciating.  The idea of pressing the buttons was too much.



I reached for the person next to me, grabbed her wrist.  Some woman with a crescent moon on a blue costume.  She gave me a startled look with a lost, shellshocked expression.  When I first pressed against the  communications button, she moved her arm, as if she thought I was guiding her movements.



``Stay still!'' I snarled at her.  When I pressed again, depressing the two buttons with my pinky finger and thumb, she held her arm firm.



I shouted into the armband, ``Clockblocker down, CD-6!  Need a teleporter to get him free, stat!''



The time freezing effect of Clockblocker's power lasted anywhere from thirty seconds to ten minutes.  How long had we spent, here, since Clockblocker had given us this momentary reprieve?  It was hard to judge the passage of time with the adrenaline, the frenetic pace of the ongoing battle.



Trickster appeared in the place of the blue moon Woman, tipped his hat at me.



``Clockblocker, in there,'' I pointed with my good hand.



Trickster frowned, looked around.



``I apologize for desecrating your body, brave hero,'' he spoke, looking down at where the cape with the trumpet icon on his chest had flopped, dead.  ``You do good work even in death.''



Was he mentally cracked?  Was he serious or was he playing around?  I suspected the latter, but kidding around and wasting time in a situation like this?



In a second, the cape was replaced by an unconscious Clockblocker.  The pane of his helmet was cracked and leaking a trail of blood.  I bent down to examine him, was pushed out of the way by someone else.  Some woman with a costume that outlined her bones, like a really good version of the skeleton costumes you saw on Halloween.  She began using her fingers to check Clockblocker's neck, and I couldn't help but suspect she was a doctor.



``Listen!'' the voice that cut through the shouts and the frantic chatter was authoritative, strong.



Armsmaster.  He had Myrddin, Eidolon and Chevalier just behind him.  People turned to listen, myself included.



``He's torn through our front line, he's taken down some of our best, and he's deliberately targeted and eliminated most of the capes who were in Bastion's group.  We have precious few left who can take a hit from this creature and survive it, and we're running low on those who can wall off another tidal wave or block his path.''



``We're not going to be able to go on with Plan A.''  The words hung in the air.



``This brute is hurt, but we don't have the resources to hold him down while we hurt him any more.  We're too tightly packed, like this, and it's too easy for him to take us down in droves.   Two or three more minutes of this, and there won't be any of us left.''



Armsmaster turned, looked up at where Leviathan stood, frozen.  He pointed up at the Endbringer with his Halberd.  ``We spread out.  The second this beast is free, he's going to look for a way out, to run and heal up what we've done to him.   So we cut him off, we slow him down and keep him from getting to any areas where he can do \emph{real} damage.''



``Eidolon is going to leave, do what he can to minimize the damage from the waves and ensure the rest of the city doesn't get leveled while we're fighting here.  The rest of us are going to slow Leviathan down best we can, take any opportunities we can to hurt the motherfucker.  In just a second, we're going to organize you guys, put the toughest and strongest closest to this bastard, space out the people who can hurt him, get the weakest ones positioned to pass on word if they see him slip past us.''



``This is our plan B.  We stall, from here on out we prioritize survival over putting this abomination down, and we fucking pray that Scion notices there's an Endbringer around and shows up before this city and everyone in it is a memory.''





