





I got my orders and left behind a bizarre scene where Armsmaster was working hand in hand with Kaiser, of all people.  Kaiser worked to build the same sort of trap that he'd imprisoned Lung in, some time ago, creating bars of metal between and around each of Leviathan's limbs, a cage tight to the body.  Rune and another telekinetic were working to bend the metal from Kaiser's shaken barrier around Leviathan's limbs and face.



It wouldn't last.  Leviathan was too big, his tail extended a long distance behind him, and it was thin and supple enough to slip through almost any barrier Kaiser could erect, strong enough that it could bend metal.  Leviathan would get free, there could be no illusions on that front.



While Kaiser worked, Armsmaster was simultaneously ensuring that he could maximize the damage delivered the second Leviathan moved again.  Gingerly, he worked with the grenades the Protectorate had liberated from Bakuda, the same explosives Miss Militia had been firing at Leviathan, and hooked them up as motion activated or proximity mines.  A complicated affair, I imagined, when your target could start moving any second, and when you couldn't fully know or understand what the individual bombs did.



In the end, though, it was still our best bet to do one final measure of damage against Leviathan before he was free to wreak havoc once more.



There were a little more than fifty of us left.  Hookwolf, Fenja, Menja, Genesis, Aegis and Manpower were among the fifteen or so standing combatants that remained and were able to go toe to toe with Leviathan.  Parian, the girl in the doll costume, had formed some massive stuffed animals – a lion and a pig that stood as tall as Leviathan's shoulder.  Tougher than they looked, according to her.  I had my doubts.  I mean, it wasn't just that they were stuffed animals, but according to Parian, this was her first fight.



Too many others were capable of delivering the hurt, but were too fragile: Browbeat, Shadow Stalker, Lady Photon, Purity, Laserdream, Brandish and others I didn't know.  The Ward with the crossbow, some guy with crimson skin.  There was a light show in the sky above as Kid Win teleported in pieces of the cannon he'd had at the bank robbery, manifesting them onto a hovering platform set directly in front of Leviathan.  He'd get anywhere from a few seconds to a minute's worth of concentrated fire with the gun firing on the highest settings, directing a beam through a gap in the bars to where Narwhal's razor sharp forcefield had opened a gap in Leviathan's neck.



Beyond those first few moments after Leviathan woke up, it would be anyone's guess.



I hurried away from the site Armsmaster had indicated to me, my right hand on my left elbow, keeping my arm from moving too much.  Sector CC-7, a block and a half South, a block West.  So strange, to think that this was an area I'd walked through a dozen times, on my way to or from the Loft.  Now I was looking at it as a battlefield, trying to figure out what routes Leviathan would take.  What things I had to watch out for – the grates leading down to the storm sewers, the rain barrel on top of one of the buildings that might or might not be intact enough to retain any water in it.  Puddles.



Stuff I could use\ldots  hardly.



It wasn't like there was any weapon I could deploy, no feature of the terrain I could use to deliver the critical blow.  This was \emph{Leviathan}.  A creature that had killed more people in the last 12 years than I had even seen in my entire life.  Seen in person, anyways.



I was scared.  A huge part of me wanted to just close my eyes and hope Leviathan didn't come, that I wouldn't have to deal with him.  It would be nice to join the three hundred and fifty thousand other Brockton Bay residents that were trusting the heroes to handle things, find a peace of sorts in surrender and helplessness.  Except I couldn't.  I'd seen firsthand how Leviathan had taken down some of the strongest capes.  I couldn't find refuge in that kind of trust anymore.  My mental and emotional resources were better spent on figuring out how to help than they were on hope.



I was hurting, too.  The only thing keeping the throb of my arm from consuming my attention was the fear.  It was a kind of grim cycle:  the pain reminded me of why I should be scared, but the emotion and the adrenaline kept the pain as this intensely unpleasant background chatter in my brain, where it might have crippled me otherwise.  It was a teetering balance that had me on edge in a way I'd never experienced to this degree.  There were probably people who lived for that hypervigilant, heart-racing, brain-going-in-overtime experience.  I wasn't one of them.



Priorities.  Back to what I was thinking about – there obviously wasn't anything to be found here that would win me a fight against Leviathan or even hurt him.  Ridiculous to think that way.  Any advantages to be gained would be ones that kept me alive.



I wiped the beads of water from my lenses with my glove, which only seemed to divide each of them into a mess of smaller droplets.  Leviathan was bigger than me, stronger, faster, tougher.  I had to think like a mouse who might run into a murderous cat at any moment.  Like prey.  Use my small size.  Hide.  I needed a position that kept me out of sight, gave me a good vantage point, but left me free to make a run for it.  A spot where I had an escape route if things got bad.  To top it off, in the event Eidolon couldn't stop the wave, I could also do with cover.



It was the sort of street you saw often enough in the Docks.  Large buildings lined either side, like giant boxes made of concrete or brick.  I could have maybe found a fire escape to climb up, in the hopes that I'd be out of reach of the wave, but my experience with Lung back on day one had taught me better.  The higher ground was an advantage, sure, but if your opponent could get up or down from that location faster and more easily than you could, that stopped being an asset really damn quickly.  If there was anything that was going to be useful, it would be on ground level.  I saw a rusted van that had sat in front of an old workshop since I'd first passed through this area, all tires flat, windows broken, interior gutted.  A chain link fence stretched between two buildings, but someone had cut the wires that connected the fence to the frame, so half of it was curled back and waving slightly in the wind and rain.



No, those things weren't useful.  Larger scale?  There was an old roof supported by two pillars, attached on one side to a building, a carport, perhaps.  The roof was mostly intact, corrugated steel with a smallish hole in one lower corner, which meant the area beneath it was largely dry, but for a small puddle.  It was also exposed on three sides, which meant I couldn't stay there.  My bugs could.  It was a place they could keep dry until I needed them.



I'd been acutely aware of my bugs since the battle started, and for the second time I could remember, I found my power was responding far more effectively as I called for them.  My reach extended further, my bugs were fractionally more responsive.  The last time this had been the case, it had been when I teamed up with Bitch, Sundancer and Newter and wound up fighting Oni Lee and Lung.  I couldn't explain it, but I wasn't going to complain.  I needed every small advantage I could get.



As they began gathering under the carport, my mind returned to that notion of being successful `prey'.



When I'd originally designed my costume, I'd picked the darker colors, made sure that the varieties of chitin I used to make the armor were spaced out so the individual shading would retain some `speckling' after being painted, all for a reason.  Camouflage.  I'd known I'd have my bugs all around me.  I'd known I would be standing in the midst of them while they gathered into swarms, would have them crawling on me from time to time.  So I'd picked darker colors and made my armor mottled to blend in with the bugs that were, obviously, specks.



Just hiding inside my swarm wouldn't be enough.  Too easy for him to attack just the one cluster, tear through me.



So I gathered more than one smaller swarm, clustering them in areas where it was dry.  The interior of the rusted van, under eaves, in doorframes and on a roof, under a large rain barrel.



Then, struck by a little inspiration, I condensed the nine swarms into human-ish shapes.  Black silhouettes crouched, stood tall with arms akimbo, leaned against walls, leaned partially outside the driver's side window of the van.  In the gloom, through the rain, it was deceptive.  Deceptive enough?  I couldn't be sure.



I felt the bite of cold air.  A chill breeze, going straight through the soaked fabric of my costume.  When I looked down to where the long road sloped to the edge of the water, I saw the reason for the chill.  Eidolon was flying at the coast, focusing blue rays on the water around the shattered boardwalk and debris at the water's edge, hardening the waves into irregular sheets and glacier-like formations of ice.



Dangerous.  I could remember seeing on TV that they'd tried something like this a few years ago.  A Tinker using an ice engine, I think.  I didn't know exactly how or why, but judging by the fact that they hadn't used the tactic again, I got the impression It had turned out \emph{really} badly.



My guess was based on the notion that hydrokinesis was the movement of water, and ice was just water in another form.  It wasn't that Leviathan would levitate the chunks of ice.  Nothing so blatant.  Rather, when a tidal wave did break through the ice, rolled up onto the battlefield with frozen shards and chunks caught up in the current, Leviathan might move those chunks a little faster in the wave's passage, make them hit a little harder, and give them a tendency to strike where they could do the most damage.



That was my suspicion, anyways.  The heroes didn't exactly dish out the full details at press conferences, afterward, so I could only make an educated guess.



Either way, it was a delaying tactic.  Holding off the damage, in the hopes that we could end this or get reinforcements before Brockton Bay became another Newfoundland.



We were hoping for Scion.  The first cape, the golden skinned man.  The guy that could go toe to toe with an Endbringer and win, if things hadn't already gone too far south.  If Behemoth hadn't already turned the area into a radioactive, magma-ridden wasteland.  If Leviathan hadn't built up enough momentum with his waves.  If the Simurgh\ldots Ok, the Simurgh was different, I had to admit.  The issue with her wasn't so much winning the battle.  It was what came after.  Win every battle against her, lose the war, more or less.



The problem with waiting on Scion was that the guy wasn't exactly in touch with the rest of us.  There was speculation he had at least one human contact – someone that had given him clothing and a costume, at least – but he never bothered to stop long enough for anyone to pass on any requests, to tell him to go to X place when we gave him Y signal.  He rescued people twenty-four-seven, three hundred and sixty five days a year, handling crises only as they came to his attention, which meant that sometimes an Endbringer came and Scion was wholly occupied with saving sinking ships, stopping landslides and putting out housefires.  I wondered what he was doing now.



My swarms were in place, which left me having to decide where to hide.  The carport was too in the open, none of the eaves left me a good enough escape route, and as for the space under the rain barrel on the roof, well, I wasn't that stupid, and I'd already dismissed the roof as an option anyways.



I started toward the rusted van.  I was halfway there when I reconsidered.  As comforting as it might be to have the safety of metal around me and to be more or less concealed, it posed some of the same problems as the rooftops.  If things turned sour or if an unexpected situation arose, I'd be trapped.



After a moment of tense consideration, I reluctantly decided on the carport, hunkering down in the gloom and hoping the shadows there would help conceal me.  It offered me an escape route – around the back of the building, or through the side door, it gave me cover from the rain and any debris, and it gave me concealment.  I'd have to cope with the lack of cover from any incoming waves or Leviathan himself.



Secure in the amount of bugs around me, I collected the ones that could go out in the rain and manage reasonably well.  Primarily roaches.  I sent them out in the general direction of where Leviathan and the others were.  The better a sense I had of any imminent encounters, the better I could react.



\emph{Manpower deceased, CD-6.  Aegis deceased}, CD-6, my armband spoke, at the same moment my bugs reached the area around where Leviathan had been.



He was awake again.



Aegis would have been covering an aerial route, keeping Leviathan from heading to the rooftops, which meant Leviathan went \emph{up.}  I had the mass of roaches ascend, trying to get a sense of his location.  I tried to use my armband to help gauge the direction he was traveling, but since I couldn't move my arm, it was difficult at best.



\emph{Fenja down,} CC-6.  My head snapped up.



I found them.  Fenja and Menja were duking it out with Leviathan.  Both were nearly as big as he was, which was saying a fair bit.  I knew their power warped geometry to make them bigger, simultaneously reduced the effective size of incoming attacks by an inversely proportionate amount.  Six times as tall and a sixth of the hurt, on top of the benefits of being bigger.



\emph{Fenja deceased, CC-6}.



It wasn't doing them a lot of good.  Not Fenja, anyways.



I saw a light as Kid Win rose above the level of the buildings, fired a painfully bright beam down at the Endbringer\emph{.  }After the laser petered out\emph{, h}e rose up higher again, to keep out of reach.  He was in the middle of firing another beam when the laser flicked around nearly three hundred and sixty degrees, spun by a massive impact.



\emph{Kid win down, CC-6.}



And then Leviathan was in view, entering the same street I was on.  As if to herald his coming, a massive wave crashed hard against the barrier of ice Eidolon had erected around the wrecked Boardwalk, the spray seemingly reaching nearly to the stormclouds above.



One shoulder was bloated, five times the normal size, twisted, like it was covered in elephantine tumors, bleeding openly.  He was injured in other places, had a hole through the side of his stomach, a larger blackened wound at the base of his neck, and a fifth of his face was missing, torn off below the cheekbone.  He didn't seem to be suffering much.  He held Kaiser's upper torso in the one claw, tossed it casually to one side.  The man's legs were nowhere to be seen.



Wait, what?  I hadn't heard the report on Kaiser's death.  I checked my armband, where my arm hung immobile at my side.



It was dead, offline.  Black screen.



I didn't have another second to worry – Leviathan was extending one claw in my general direction.



The water that had pooled shallowly beneath the carport trickled his way, as if it were moving downhill, gathered in a rising bulge of water on the street in front of the carport, swelling to five feet in height, fifteen feet across.



Unsure what to do, I remained absolutely still.



A movement of his claw, and the bulge broke, spilled to one side as an onrushing wave.  It swept beneath the rusted van, suddenly rose to heave the vehicle in Leviathan's direction.  The van rolled once, skidding toward the Endbringer, threatening to strike one leg out from under him.  He stopped it by punching it through the roof, into the front end of the van.  He stabbed the other claw through at the same point, tore the van into two halves that he tossed to either side of him.



A flick of his tail, and he sent a blade of water slashing through the air at the rain barrel, slicing through the swarm and stilts.  The barrel crashed to the rooftop, and water cascaded out.  A twisting movement of his claw, and that cascade of water flowed off the roof in a small, controlled wave, moving like a speeding car, straight towards the carport on the other side of the street, toward \emph{me}.



I caught a glimpse of Leviathan rearing back in reaction to something as I legged it, left my swarm behind as I ran perpendicular to the wave's direction, away from Leviathan.  I leaped as I felt it make contact with the swarm, felt it slam into my legs a fraction of a second after.



I'd cleared enough ground that the angle of the hit didn't throw me straight into the side of the building.  I \emph{was} thrown a distance, rolled on my side, on top of and over my probably-broken arm.



Pain consumed me.  I writhed, my good hand pressing on my bad arm.  I gagged, pulled my mask up to throw up, as if my body was trying to find some way to rebel against the pain.  I tried to climb to my feet, but I was too weak, dizzy, and my good arm gave out.  I landed face first in dirty water.



I had no idea how long it took me to pull myself together.  It could have been two minutes, it could have been ten seconds.  I managed to climb to my feet.  Stumble back toward the carport, staying to the shadows.



As I approached the corner of the building, I saw Armsmaster fighting toe to toe with Leviathan, a Halberd in each hand.  One was similar to the one he'd used the night we attacked the fundraiser, capable of unfolding into a grappling hook, the other was simpler, a dull stainless steel from tip to butt end, with no decoration or style to it.  The head was surrounded by a strange blur that seemed static, unmoving around the blade and point.



Leviathan slapped his tail at Armsmaster's legs, and Armsmaster leaped over it, swiped out with the blurry Halberd.  It carved a chunk out of Leviathan, left a cloud of dust that the rain quickly drove down into the expanse of water beneath them.  The Endbringer reared back in pain, and Armsmaster stepped forward, leaped up higher than any normal human could, and caught Leviathan just above the knee with the Halberd, driving the blade nearly a third of the way to the bone.



Leviathan retaliated, swiping at Armsmaster, but the hero planted a foot on the uninjured part of the knee, and kicked himself back and out of the way.  The afterimage followed him, and he swiped at it with the other Halberd.  The blade erupted with a flame like a giant purple blowtorch, turning the worst of the afterimage into steam before it could crush him.  He turned his back so the steam didn't billow against the exposed flesh of his face.  Some remains of the afterimage struck his armor, but he slid back and rolled with the impact, keeping his feet on the ground the entire time, enabling him to leap and roll to one side as Leviathan's tail came down from behind and directly above him.



Leviathan was badly injured.  Ichor poured from six large wounds that hadn't been there when he'd arrived on the street.



``You dumb brute,'' Armsmaster growled.  He was panting for breath.  ``Every fight you've done so far, that we've got on camera?  I've watched it, put it through programs.  I've got a computer on my back that's relaying to a supernetwork, noting your every move, using subsonic pulses to read every aspect of the street, the surrounding buildings, every feature of the terrain.  I know exactly what you're going to do next – you're going to try to catch me from behind with a wave.''



Leviathan lunged, swiped with the oversized claw.  Armsmaster rolled to one side, then swung both Halberds behind him to intercept the wave that was coming from behind, vaporize it.



``You don't even speak English, do you?  Or you'd know what I was saying, you'd know I already won.  The others helped, slowing you down, stopping the waves.  But this victory, this killing blow?  It's going to be \emph{mine}.''



Leviathan lunged, stopped, letting his water echo get ahead of him, then lunged again, a half second later.  Armsmaster leaped out of the way of the echo, drew his knees to his chest to avoid a claw swipe while he was still airborne, and sent his grappling hook between Leviathan's feet to pull himself to the ground in a flash.  He skidded with the momentum, right between Leviathan's legs, and raised the blurry Halberd to strike Leviathan between the legs, against the first ten feet of Leviathan's tail.  The tail was turned to dust where the blade made contact, the plumes of it briefly obscuring Armsmaster.



``This cloud around my blade?  Nanotechnology.  Nano-structures engineered to slide between atoms, sever molecular bonds.  Cuts through anything.  Everything.  Like a sharp knife through air.''



Leviathan whipped his tail at Armsmaster.  Armsmaster stepped out of the way, slapped at the tail with the broad side of the blade.  More dust, another chunk of flesh gone, ichor pouring from the injury.  He ducked the echo as though it were an idle afterthought.



Leviathan turned to run.  Armsmaster sent out one blade like a grappling hook, circled the smaller of the Endbringer's claws with the chain.  Leviathan moved, oblivious or uncaring, and Armsmaster waited until the slack was out of the chain, pressed a button.



The chain and Halberd ceased moving, and even Leviathan's strength ceased to move it.  Rather than pull away, the Endbringer skidded, fell on his back, wrist still held by the chain.



A half second later, the chain went briefly slack, then rigid again as Armsmaster reeled himself in. He drove the blurry blade straight into Leviathan's face with all the force of his forward momentum.  He pulled it free, slashed again, then freed the chain and used it to pull himself across the street, out of reach of Leviathan's violent response.



Armsmaster called out, ``Let's see how quickly you respond to classical conditioning.  Every time you try to run, I'll do something like that.''



Leviathan had no reply.  He simply climbed to his feet, swiped a claw through the air.  Armsmaster parried the afterimage that sailed through the air toward him, using the purple flame.



``For the record, that last trick was a temporal stasis trigger, with thanks owed to the cooperation of a subordinate of mine.  Drains my battery reserves, but you don't understand that, do you?''



Leviathan lunged, and Armsmaster fired out the grappling hook, stopped it in mid air by freezing it in time.  Leviathan ran himself through on the chain, the thing spearing deep into his neck and out the back of his torso.  Uncaring, the Endbringer continued to charge at Armsmaster.



Armsmaster let the chain go slack, ducked a swipe of the tail, leaped forward and to one side to avoid the claw that followed.  Another small hop and roll ensured he moved right beneath the afterimage, and he made two swipes with the blurry Halberd at the back of Leviathan's thighs as he passed behind the Endbringer.  His chain reeled in, pulled free of Leviathan's neck wth a spray of blood, came down and across Leviathan's hip to snap back to the top of the Halberd.  He fired it off again to get himself more distance, pulling himself across the street, spinning to face Leviathan once more as he stopped.



He passed one Halberd to the other hand, so he held two, wiped some frothing spittle from his mouth with his gauntlet.  ``\emph{I} am going to be the one to take your head, abomination.  I can only hope you know mortal terror in your last moments, know what you've inflicted on so many others.''



Leviathan stood, straighted itself, touched its claw to its ruined face, then its neck.  The amount of blood it was losing – it seemed somehow more than Leviathan should have been able to contain within himself.  I mean, he was big, but this was a \emph{lot} of blood.



For several long seconds, Leviathan didn't move.



``Delaying, buying time for a tsunami?'' Armsmaster laughed, and Leviathan cocked his head at the display of emotion.  ``No.  Three point four minutes before the next big wave breaks through the ice.  Dragon's probes are giving me the data on that.  This will be over before then.''



He stepped forward, then stepped again, waiting for some cue from Leviathan.  On Armsmaster's third step, Leviathan took a small step back, lashed his tail behind him.



``Finally scared?'' Armsmaster taunted.  ``Good.''



Nausea and pain was welling up in me again as I watched from the corner of the building, under the carport, threatening to override my sense of awe.  It was all I could do to keep quiet, keep from distracting Armsmaster, or distracting Leviathan and throwing some wrench in Armsmaster's data.  The last thing I wanted was to become the hostage that made Armsmaster hesitate for the fraction of a second that cost him -cost us all-  the fight.



Armsmaster went on an all-out offensive, slashing as fast as his arm could move, cutting leg, knee, tail, leg again, moving out of the way of Leviathan's attacks as though it were easy.  For ten seconds he continued, relentless.



``I should thank you, monster,'' Armsmaster spoke, after he'd just finished a backflip that had carried him near enough to Leviathan's torso to strike the creature across the lower belly.



Leviathan lunged, dropping to all fours, as if trying to swamp Armsmaster with a huge volume of water by way of his afterimage.  Armsmaster was already casting his grappling hook out, pulling himself out of the way.  In the final moment before he pulled away, his other Halberd swung up and into Leviathan's neck, making a wound mirroring the spot where Narwhal's forcefield had cleaved deep, the one Kid Win had undoubtedly opened wider with his laser turret.  Armsmaster reeled the hook back in.



The Endbringer turned, as if to run, only for the loop of the grappling hook's chain to pass under his `chin'.  Armsmaster heaved himself up and onto the Endbringer's back, drove the Halberd into one side of the neck, lengthening the cut he'd just made.  He stepped on the top of the Endbringer's head, leaped down, catching the Endbringer across the face with the Halberd as he descended.  Leviathan collapsed, going spread-eagle.



Armsmaster slashed at Leviathan's forearms as the Endbringer started to climb to his feet.  More damage done, though it didn't stop Leviathan from rising.  While Armsmaster pressed the attack, his armband hissed with a message I couldn't make out.  I glanced at mine – still broken.



``This will be over before then,'' Armsmaster echoed an earlier statement, speaking more to himself than to the armband or Leviathan.



Leviathan hopped backwards to create some distance, staggered a little as the more injured of his two legs failed to take his weight, used his smaller hand to stop from falling a second time, poising himself on three limbs.



Armsmaster used his grappling hook to haul himself close, readying to make another slash for the neck.  He changed his mind as the ground rumbled, pulled the hook free to latch it on a garage door.  Countering his forward momentum, he swung himself to one side of the road, staying out of Leviathan's reach.



The ground rumbled again, brief, intense, stopped.



Armsmaster touched a hand to the side of his visor, and I thought I saw his lips crease in a frown before he turned his head away from me.



Another fierce rumble, and a crack appeared like a seam down the center of the street, a straight line as far as I could see in either direction.



Leviathan raised his claw, and the road suddenly split, heaving upward as a concrete pipe wide enough to fit a man crested from the pavement like a whale rising from the waves.  A second later, water gushed forth, veering toward Armsmaster.



\emph{The storm sewers}.



Armsmaster hesitated, then threw his grappling-hook-Halberd forward into the onrushing waves like a javelin.  The gush of water froze in time, and he leapt forward, stepping on the furthermost extensions of the immobile spray in a parkour-style ascent over the water and the pipe.  The water resumed its regular motion as Armsmaster took his final leaping step off the top, heading straight for Leviathan.



Leviathan moved faster than he had in the last minute, caught the blade in his claw.



Dust rose from the claw as the blade sank deep, blood poured out, but the blade remained fixed in place.  Armsmaster tugged, failed to dislodge it.  He tried to pull away, but I could see Leviathan had caught onto his hand and wrist with his clawtips, while the Halberd sat embedded in his `palm'.



``How!?'' Armsmaster roared.



I didn't hesitate a moment in sending out my bugs.  Three swarms, shaped like people, more as a general cloud.  The bugs all sagged beneath the drenching rain, the ones on top taking the brunt of the downpour.



Leviathan planted one foot beside Armsmaster for balance, reached out with his free claw, and pressed the tips against the side of Armsmaster's throat and torso.  Still holding on to Armsmaster's hand and wrist, he pushed against the side of the man's body.  Armsmaster screamed, a frantic noise that seemed to redouble in urgency with every breath.  He tipped over and fell with a splash.



The Endbringer stood, showing none of the frailty or pain it had been displaying seconds ago.  The injuries were there, to be sure, his head hung at an angle because of the way the weight of his head hung on the intact portions of his neck, but he wasn't suffering, had no trouble putting his full weight on his more injured leg.  Had it been an act?



The Endbringer dropped Armsmaster's arm and Halberd, where the weight of the metal armor and device pulled them beneath the water.  A lash of his tail dispatched two of my three swarms.  He watched, seeming not to care, as the third ran up to him, smashed against his leg.  The bugs spreading out, burying themselves deep into his injuries. I was hoping to find some weakness, devour him from the inside out, but the bugs might as well have been biting on steel.  Nothing budged beneath their jaws, their stings couldn't penetrate.



He turned, crouched, bolted West, away from the coast, full speed.



I hurried to Armsmaster's side.



``You,'' he groaned.  His left arm was gone at the shoulder, torn out of the socket.  Blood poured from the wound.  ``You're dead.''



``Hey, you're not making any sense.''



``He killed you.''



Had my armband announced my death when it glitched out and died?  Assumed total destruction of my unit, and me with it?



``I'm alive.  Listen, I'm going to try and find your arm, my armband got broken, maybe something got dislodged when Leviathan broke my arm.''



He only groaned unintelligibly in response.



I ran over to the general area where Leviathan had dropped Armsmaster's arm.   I tripped over the crack that ran down the middle of the street, got my feet under me to keep running, and began feeling through the water.



I came within inches of touching the submerged blade, turning my hand to molecular dust.



Finding the arm, I picked it up.  Heavy, almost too much to hold in one hand.  It wasn't just the weight of the armor or the fact that it was a muscular, full-grown-man's limb – the gauntlet had been crushed around the pole of the Halberd, crumpled like tinfoil.  With the arm and weapon in a bricklayer's grip that was painful to maintain, I hurried back to Armsmaster's side, dropped them near him.  I shook him, hoping to get him alert, to no avail.



With my only working hand, I pried the Halberd free of his glove, rested his arm across his chest, and pressed the button.



``Armsmaster down!  CC-7!  Leviathan is heading West\ldots''



I felt the bugs I'd clustered in Leviathan's wounds change direction.  The compass point between West and Northwest was what?  More Wests than North.



``Cancel that!  He's going West-North-West from my location!''



My voice echoed back to me in the Armband's tinny voice a half-second after I'd finished.  Armsmaster's armband changed to display a red dot, tracking Leviathan's movements, or the closest approximation the system could guess.



``Roger, sounds like he might be heading for one of the shelters, lots of people packed into a space where they can't run, vulnerable,'' someone replied, ``Medical help incoming.  Whoever this is, you can track Leviathan?''



``Yes, as long as I'm within a few blocks of him.''  Again, the system relayed my message. \emph{Affirmative.  Range restriction of `a few blocks'}.



Did it really need to reword what I said?



``Can you fly?  Chase him?''



``No.''  \emph{Negative}.



``Then I'm sending a flier your way, to ensure you stay close enough.  We need eyes on this bastard, and you're them.''



``Got it!''



There was only silence after that.  Teeth clenched, shivering, I pressed my good hand as hard as I could manage against the ragged mess of Armsmaster's shoulder, trying to slow the blood loss.





