





Lady Photon and the eighteen year old Laserdream landed beside Armsmaster, making a small splash as they touched down.



You could see the family resemblance.  They weren't supermodel good looking, but they were attractive people, even with their hair wet and plastered to their heads and shoulders by the rain.  Both wore costumes with a white base color, had heart shaped faces, full lips and blonde hair.  Lady Photon's costume sported a starburst on her chest, with several of the lines extending around her body, or down her legs, going from indigo to purple as it got further from the center.  Her hair was straight, shoulder length, held away from her face by a tiara shaped much like the same starburst image on her chest.



Her daughter had a stylized arrow pointing down and to her right, on her chest, with a half dozen lines  trailing behind it, over her left shoulder, one line zig-zagging across the others.  The entire design gradually faded from a ruby red to a magenta color in much the same way her mom's did.  Similar rows of lines with the zig-zag overlapping them ran down her legs and arms.  She didn't dye her hair in her `color' like her younger brother did -had, past tense-, or wear the tinted sunglasses, but she did wear a ruby red hairband over her wavy hair, to ensure she always had a coquettish sweep of hair in place over one eye, and to pull the magenta, red and white color scheme together.



More than anything else, though, the two of them had the look of people who had seen half their immediate family brutally and senselessly torn apart over the course of one terrible hour.  As though they'd had their hearts torn out of their chests and were somehow still standing.  It wasn't that I had seen anyone in those circumstances before, but that look existed, and they had it.



It was painful to look at.  It reminded me of when my mom had died.  I'd been in a similar state.



Lady Photon – Photon Mom to Brockton Bay residents and the local news media – bent down by Armsmaster.  She created a shaped forcefield tight against his shoulder, lifted him with a grunt.



``Take him,'' Lady Photon's voice was strangely hollow, though firm.



``No.  I'm a better flier, and more likely to hurt that thing in a fight.  I'll take the girl and help against Leviathan.''  Laserdream had a little more life in her voice than her mother did.



\emph{The girl}.  Like I didn't warrant a name, or it wasn't worth the effort to remember.  A part of me wanted to stand up for myself, a larger part of me knew this wasn't the time or place.



After a long few seconds of deliberation, Lady Photon nodded.  She looked like making that decision aged her years.



Laserdream and her mom looked at me.  I felt like I should say something.  Give condolences?  Tell them that their family had died well?  I couldn't think of a way to put it that didn't tell them something they already knew, or anything that wouldn't sound horribly offensive or insincere coming from a villain.



``Let's go get that-'' I stopped, both because I suddenly felt that something like \emph{motherfucker} was too crass, and because I wanted to bend down to pick up Armsmaster's Halberd, the one with the disintegration blade, grabbing the pole of it with my good hand. ``Let's go get him,'' I stated, lamely.



It took some doing for Laserdream to lift me without pressing against my broken arm or touching the blade. She wound up holding me with an arm under my knees and the crook of her elbow at my neck.  She held the Halberd for me.  I resigned myself to being cradled – there was no dignified way to be carried.  She had morning breath, a strangely mundane thing – she'd likely been woken up at half past six in the morning by the sirens, hadn't had time to brush her teeth or eat before coming here.



She took off, smooth.  It felt like an elevator kicking into motion, except we kept going faster, had the wind in our faces.



My first time flying, if you discounted the experience of riding a mutant dog as it leapt from a building, which was sort of half-flying.  It wasn't half as exhilirating as I'd thought the experience would be.  Tainted by the sombre, tense mood, the sting of the rain and the bitter chill that went straight through my damp costume and mask.  Each time she adjusted her hold on me, I had to fight that deep primal instinct that told me I was going to fall to my death.  She was adjusting her grip a lot, too – she didn't have superstrength, and I couldn't have been easy to carry, especially soaking wet.



My power's range was almost double the usual, and I had zero clue as to why.  I wasn't about to complain.  Using Laserdream's armband and my right hand, I passed on details.



``He's at CA-4, heading Northwest!''



The roads beneath us were damaged, shattered.  When Leviathan had shifted the position of the storm sewers, he'd gone all out, and he'd gone a step further than just the storm sewer – he'd also torn up the water supply network for the city.  The occasional pipe speared up between the slats in the sidewalk, fire hydrants were dislodged, and the water that poured from these was barely a trickle now.  That might have meant too much was leaking from the damaged pipes to give the water any pressure.



As he'd beaten a path deeper into the city, he had found opportunities to do damage on the way.  A police car had been thrown through the second story of a building.  A half block later, as he'd rounded a corner, he had elected to go through the corner of a building, tearing out the supporting architecture.  The structure had partially collapsed into the street.



We passed over a gas station he'd stampeded through, and Laserdream erected a crimson forcefield bubble around us to protect us from the smoke and heat of the ongoing blaze.



``BZ-4,'' I reported.  Then I saw movement from the coast, called out through the armband's channels, ``Wave!''



I was glad to be in the air as the tidal wave struck.  The barrier of ice and the wreckage at the beaches did a lot to dampen the wave's effect, but I watched as the water streamed a good half-mile into the city.  Buildings collapsed, cars were pushed, and even trees came free of the earth.



No cape casualties announced from Laserdream's armband, at least.



We passed over the Weymouth shopping center.  It had been devastated by Leviathan's passage, then had largely folded in on itself in the wake of the most recent wave.  From the way the debris seemed to have exploded out the far wall, it didn't look like Leviathan had even slowed down as he tore through the building.  That wasn't what spooked me.



What spooked me was that I'd been through the Weymouth shopping center more than a hundred times.  It was the closest mall to my house.



When I sensed Leviathan turning south, towards downtown, I didn't feel particularly relieved.  There were enough shelters and enough space in the shelters to handle virtually every Brockton Bay resident in the city proper.  From what I remembered, not everyone had participated in the drills that happened every five years or so, choosing to stay home.  It was very possible that some shelters near the residential areas might prove to be over capacity, that my dad, if he arrived late, might have been redirected to another shelter.  One closer to downtown, where Leviathan was going.  I couldn't trust that he was out of harm's way.



``He's at or near BZ-6, heading south.''



The area we were entering had been further from the heroes with the forcefields, where waves hadn't had their impact softened or diverted by the the PHQ's forcefield or the larger, heavier, blockier structures of the Docks.  Entire neighborhoods had been flattened, reduced to detritus that floated in muddy, murky waters.  Larger buildings, what I suspected might have been part of the local college, were standing but badly damaged. Countless cars sat in the roads and parking lots with water pouring in through shattered windows.



Laserdream changed course, to follow Lord street, the main road that ran through the city and downtown, tracing the line of the bay.



``What are you doing?'' I asked her.



``The wreckage goes this way,'' she responded.



I looked down.  It was hard to tell, with the damage already done, the water flooding the streets, but I suspected she was right.  One building that looked like it should have stood against the waves thus far was wrecked, and mangled bodies floated around it.  It \emph{could} have been the tidal wave, but it was just as likely that Leviathan had seen a target and torn through it.



``Maybe, but he might have been faking us out, or he detoured further ahead,'' I said.  I pointed southwest.  ``That way.''



She gave me a look, I turned my attention to her armband, tried to discern where Leviathan fell on the grid.  Around the same moment I figured it out, I felt him halt.  ``BX-8 or very close to it!  He's downtown, and he just stopped moving.''



``You sure?'' came Chevalier's voice from the armband.



``Ninety-nine percent.''



``Noted.  We're teleporting forces in.''



Laserdream didn't argue with me.  We arrived at the scene of the battle a matter of seconds later.  Familiar territory.



I had been near here a little less than two hours ago.  The skeleton of a building in construction was in view, a matter of blocks away, an unlit black against a dark gray sky.  Beneath that, I knew, was Coil's subterranean base of operations.



Parian had given life to three stuffed animals that lumbered around Leviathan.  A stuffed goat stepped forward, and sidewalk cracked under a hoof of patchwork leather and corduroy.  A bipedal tiger grabbed at an unlit streetlight, unrooted it, and charged Leviathan like a knight with a lance couched in one armpit.  The third, an octopus, ran interference, disrupting Leviathan's afterimages before they could strike capes and wrapping tentacles around Leviathan's limbs if he tried to break away.  Parian was gathering more cloth from the other side of a smashed display window, drawing it together into a crude quadruped shape, moving a series of needles and threads through the air in an uncanny unison that reminded me of my control over my spiders.



Leviathan caught the streetlight `lance' and clawed through the tiger's chest, doing surprisingly little damage considering that it was just fabric.  After three good hits, the tiger deflated explosively.



The octopus and goat grappled Leviathan while Purity blasted him with a crushing beam of light.  By the time he recovered, Parian was inflating the half-created shape in front of her, so it could stumble into the fray.  She turned her attention to repairing the `tiger'.



I was curious about her power.  Some sort of telekinesis, with a gimmick?  She had a crapton of fine manipulation with the needles and threads, that much was obvious, but the larger creations she was putting together – whatever she was doing to animate them with telekinesis or whatever, it left them fairly clumsy.  Did her control get worse as she turned her attention to larger things?  Why manipulate cloth and not something stronger, sturdier?



I wondered if she was one of the capes that thought of what she did as being `magic'.  Her power was esoteric enough.



A slash of Leviathan's tail brought down two of the stuffed entities, and Hookwolf tackled him to ensure the Endbringer didn't get a moment's respite.  Leviathan caught Hookwolf around the middle with his tail, flecks of blood and flesh spraying from the tail as it circled Hookwolf's body of skirring, whisking blades.  Leviathan hurled Hookwolf away.



Browbeat saw an opening, stepped in to pound Leviathan in the stomach, strike him in the knee Armsmaster had injured.  Leviathan, arms caught by Parian's octopus and goat, raised one foot, caught Browbeat around the throat with his clawed toes, and then stomped down sharply.



\emph{Browbeat down, BW-8}.



Leviathan leaned back hard, making Parian's creations stumble as they maintained their grip, then heaved them forward.  The `octopus' remanied latched on, but the `goat' was sent through the air, a projectile that flew straight for Parian.



Her creation deflated in mid air, but the piles of cloth that it was made of were heavy, and she was swamped by the mass of fabric.  Leviathan darted forward, held only by her octopus, and the afterimage rushed forward to slam into that pile of cloth.



\emph{Parian down, BW-8}.



All of the `stuffed animals' deflated.



The girl with the crossbow and Shadow Stalker opened fire, joined by Purity from above.   Laserdream dropped me at the fringe of the battlefield with the Halberd before joining them, flying above at an angle opposite Purity's, firing crimson laser blasts at Leviathan's head and face.  Leviathan readied to lunge, stopped as a curtain of darkness swept over him, the majority dissipating a second later, leaving only what was necessary to obscure his head.  It took Leviathan a second to realize he could move out of that spot to see again, a delay that earned him another on-target series of shots from our ranged combatants.  Grue was here, somewhere.



It wasn't much, I didn't have many bugs gathered here yet, but I was able to pull some together into humanoid forms.  I sent them moving across the battlefield towards Leviathan.  If one of them delayed him a second, drew an attack that would otherwise be meant for someone else, it would be worth the trouble.



I looked around, trying to find Brandish, Chevalier, Assault or Battery, or even someone tough.  Someone that could take the Halberd and make optimal use of it.



One of crossbow-girl's shots, like a needle several feet in length, speared under the side of Leviathan's neck, out the top.  Shadow Stalker's shots, at the same time, failed to penetrate Leviathan's hard exterior.



``Flechette!  I'm getting closer!'' Shadow Stalker called out, looking back at her new partner.



``Careful!'' the crossbow-girl – Flechette, I took it – replied, loading another shot.



Shadow Stalker timed her advance with a pounce on Hookwolf's part.  Empire Eighty-Eight's most notorious killer latched onto Leviathan's face and neck, blood spitting around where the storm of shifting metal hooks and blades made contact with flesh.  Shadow Stalker ran within twenty feet of the Endbringer, firing her twin crossbows.  The shots penetrated this time, disappearing into Leviathan's chest, presumably fading back in while inside him.



Flechette fired a needle through Leviathan's knee, and the Endbringer's leg buckled.  He collapsed into a kneeling position, the knee striking the ground.



Leviathan used his claws to heave Hookwolf off his face, tore the metal beast in half, and then threw the pieces down to the ground, hard.  One landed straight on top of Shadow Stalker, the other almost seemed to bounce, rapidly condensing into a roughly humanoid form before it touched the ground again, landing in a crouch.  Hookwolf backed away, the blades drawing together into a human shape, skin appearing as they withdrew.  He brought his hand over his head and pointed forward at Leviathan.  A signal for the next front-liner.



\emph{Shadow Stalker down, BW-8}.



I didn't recognize the next cape to charge in to attack.  A heroine in a brown and bronze bodysuit.  She flew in low to the ground, gathered fragments of rock and debris around her body like it was metal and she was the magnet, then went in, pummeling with fists gloved in pavement and concrete.



You could tell, almost right away, the woman didn't have much training or experience.  She was used to enemies that were too slow to move out of her way, who focused their attention wholly on her.  Leviathan ducked low to the ground, letting the heroine pass over him, then leapt for Flechette.  In the very last fraction of a second, the girl flickered, and was replaced by the brown-suited cape, who took the hit and stumbled back, fragments of rock breaking away.  Flechette dropped out of the sky where the cape had been, landed hard.  It took her a few seconds to recover enough to fire another bolt at Leviathan, strike him in the shoulder.  Trickster had just spared brown-suit from making a fuck-up that got someone killed.



The boy with the metal skin formed one hand into an oversized blade, as long as he was tall, managed a solid hit at Leviathan's injured knee as the Endbringer whirled around to face Flechette.



Leviathan slapped the teenage hero down, swiped at one of my swarm-people, then was forced down onto all fours as Purity struck him square between the shoulderblades with a column of light.  A metal shelving unit shot from the interior of a store, Ballistic's power, I was almost positive, and made Leviathan stumble back.



We had the upper hand, but that wasn't necessarily a good thing.  More than once, in the past hour alone, the Endbringer had demonstrated that any time the fight was going against him, he'd pull out all the stops and do something large scale.  A tidal wave or tearing up the streets.



We did \emph{not} have what it took to withstand another wave.  No forcefields, no barriers.



I had one of my gathered swarms explode into a mass of flying insects as they got close enough to Leviathan, make their way against the drenching rain to rise up to Leviathan's face.  Many clustered in the recessed eye sockets that looked like tears or cracks in his hard scaled exterior.  Others crawled into the wounds other capes had made.



Briefly blinded, he shook his head ponderously, using his afterimage and one swipe of his claw to clear his vision.  He scampered back as his sight was obscured yet again by one of Grue's blasts.



He lunged forward, stumbling into and out the other side of the cloud of darkness.  A swipe of his tail batted the metal-skinned boy away.  Another strike dispatched Brandish, who was moving in to attack with a pair of axes that looked as though they were made from lightning.



\emph{Brandish down, BW-8}



Flechette fired one needle into the center of Leviathan's face, between each of his four eyes.  It buried itself three quarters deep, speared out the back of his head.



He reared back, as if in slow motion, stumbled a little.  His face pointed to the sky.  He teetered.



Yeah, no.  Much as I'd like to to be, there was no fucking way it was going to be that easy.



That top-heavy body of his toppled forward, and it was only his right claw, slamming down to the pavement, that stopped his face from being driven into the ground.  The impact of his claw striking the ground rumbled past us.



The rumble didn't stop.



``Run!'' I shouted, my cry joining the shouts of others.  I turned, sloshed through the water to get away, not sure where to get away \emph{from}, or \emph{to}.



Leviathan and the ground beneath him sank a good ten feet, and water swirled and frothed as it began pouring to fill the depression.  He used his arm to shield himself as Purity fired another blast from above.  As the ground beneath him continued to sink, the water lapped higher and higher around him.



The Endbringer descended, and the area around him quickly became a massive indent, ten, fifteen, thirty, then sixty feet across, ever growing.  The force of the water pouring into the crater began to increase, and the ground underfoot grew increasingly unsteady as cracks spread across it.



I realized with a sudden panic, that I wasn't making headway against the waves and the ground that was giving way underfoot.  The growing crater was continuing to spread well past me, rising above me as the ground I stood on descended.



``Need help!'' I screamed, as water began falling atop me from a higher point, spraying into me with enough force that I began to stumble back, fall.



The ground in front of and above me folded into a massive fissure.  The movement of the cracked sections of road created a torrent of water that washed over me, engulfed me and forced me under.  The impact and pain from the force of the water on my broken arm was enervating, drew most of the fight out of me when I very much needed to be able to struggle, get myself  back above the surface.  I tried to touch bottom, to maybe kick myself back up, but the ground wasn't there.  Feeling out with the pole of the Halberd, I touched ground, pushed, failed to get anywhere.



A hand seized the pole of the Halberd, heaved me up, changed its grip to my right wrist and pulled me up and free of the waves.



When I blinked my eyes clear of water, Laserdream was above me.  She faced the epicenter of the growing depression in the ground, flying backwards.  Her other hand clung to an unconscious Parian.  It seemed like the two of us were too much for her to carry alone, because she hurried straight for a nearby rooftop, carefully lay Parian down.



We hadn't set down for more than ten seconds before the building shuddered and began to collapse.  The ground beneath the building cracked and tilted, no doubt because the underlying soil and rock was being drawn away by churning water.  The flooding in the streets was diverted into the deepening bowl-shaped cavity Leviathan was creating, filling it.  It was almost a lake, now, three city blocks across and growing rapidly. Only fragments of the taller buildings in the area stayed above the waves; some buildings were already toppled onto their sides, others half-collapsed and still breaking apart as I watched.  Some capes were climbing out of the water and onto the ruined buildings, with the help of the more mobile capes.  Velocity and Trickster were working in tandem, Velocity running atop the water's surface to safe ground, trickster swapping him for someone who was floundering, rinse, repeat.



As our footing dropped beneath us, Laserdream reluctantly grabbed at my hand and Parian's belt, hauled us back up into the air.



Above me, her armband flashed yellow.



``Armband!'' I called up to her. ``Tidal wave?''



``Can't see unless I drop you,'' she responded, over the dull roar of the waves beneath us.  With a bit of sarcasm and harshness to her tone, she asked me, ``\emph{Do} you want me to drop you?''



Right, I'd kind of messed with her cousins at the bank robbery.  She counted me as an ally, here and now, but she wouldn't be friendly.



Myrddin and Eidolon moved from the coast to the `lake' in the upper end of Downtown.  I saw and sensed Leviathan leap from the water like a dolphin cresting the waves, moving no less than two hundred feet in the air, toward the pair, lashing out with his afterimage in every direction.



I didn't see how it turned out, because Laserdream carried Parian and me away.  I could sense the Endbringer through the bugs that had made their way deepest into his wounds, the ones that had found spots where his afterimage couldn't flush them out each time it manifested.  With my power, I could track him beneath the water.  He was moving so fast that it was almost as though he were teleporting, finding the drowning and executing them.



\emph{Scalder deceased, BW-8.  Cloister deceased, BW-8.  The Erudite deceased, BW-8.  Frenetic deceased, BW-8.  Penitent deceased, BW-9.  Smackdown deceased, BX-8.  Strider deceased, BW-8}



``Setting down again,'' Laserdream said.



``But if there's a tidal wave-''



``I don't see one.''



I joined her in looking toward the coast.  The water was as stable as it had been since the fight started.



``If it's a trick-''



With a little anger in her voice, a hard tone, she spoke, ``Either we set down or I drop you.  I can't hold on much longer.''



``Right.''



She carried me two blocks away from the crater.  The ground was wet, but no longer submerged, the road was torn up, shattered, covered with debris.



Laserdream checked her armband, ``It's one of the shelters.  They sprung a leak, need help evacuating.  I'm going.''



\emph{Dad}.  It could be my dad.



``Bring me,'' I said.



She frowned.



``I know your arms are tired.  Mine is too, and I was just hanging there.  I can't tell you how thankful I am that you've done this much to help me, but we have to stick together, and you can fly low enough to the ground that you can drop me if you have to.''



``Fine, but we're leaving the doll kid here.''



She laid Parian down in a recessed doorway, then pressed the `ping' button on the girl's armband.



I held the Halberd out while Laserdream walked around behind me.  She wrapped her arms around my chest and lifted us off.  Uncomfortable, and she was jarring my broken arm, which hurt like a motherfucker, but I couldn't complain after just having asked to come.



\emph{Myrddin down, BX-9}\emph{.}



Laserdream carried us around the edge of the `lake' that was still growing, if not quite so fast as it had been.  I saw others gathered at the edge of the water, forming battle lines where Leviathan might have a clear path to make a run for it. \emph{If} he wanted to make a run for it.  As it stood, he was entirely in his environment, in the heart of the city, where he could continue to work whatever mojo he needed to bring more tidal waves down on our heads.  To my bug senses, Leviathan was deep beneath the waves, moving rapidly, acting like he was engaged in a fight.  Against Eidolon?  I couldn't tell.  Every darting, hyperfast movement dislodged a few bugs, made him harder to detect.



The shelter was set beneath a smallish library.  A concrete stairwell beside the building led belowground to the twenty-foot wide vault door.  Fragments of the building and the ledge overhanging the stairwell had fallen, blocked the door from opening fully.  Making matters worse, the door was stuck in a partially ajar position, and the stairwell was flooded with water, which ran steadily into the shelter.  Two capes were already present, shoulder deep in the water, ducking below to grab stones and rising again to heave them out.



``What's the plan?'' I asked, as Laserdream set us down, I immediatelly sent out a call to summon bugs to my location, just to be safe.  ``Do we want to shut the door or open it?''



``Open it,'' one of the capes in the water said.  He ducked down, grabbed a rock, hauled it out with a grunt.  ``We don't know what condition they're in, inside.''



Laserdream stepped forward and began blasting with her laser, penetrating the water and breaking up the larger rocks at the base of the door.



I was very nearly useless here.  With one hand, I couldn't clear the rubble, and my power wasn't any use.  There weren't even many crabs or other crustaceans I could employ in the water around us, and the ones that did exist were small.



Then I remembered the Halberd.



``Hey,'' I stopped one of the capes that was heaving rocks out of the stairwell, ``Use this.''



``As a shovel?'' he looked skeptical.



``Just try it, only\ldots don't touch the blade.''



He nodded, took the Halberd, and ducked beneath the water.  Ten seconds later, he raised his head, ``Holy shit.  This works.''



``Use it on the door?'' I suggested.  He gave me a curt nod.



\emph{Enemy location unknown, }I could hear the cape's armband announce.  \emph{Defensive perimeter, report}.



There was a pause.



\emph{No reports.  Location unknown.  Exert caution.}



``I'm going to try cutting the door off,'' the cape spoke.  He descended beneath the water.  I could barely make out his silhouette.  Laserdream ceased firing as he made his way to where the heavy metal door was, stepped around and set to burning long channels in the side of the stairwell.  I realized it was intended to give the water in the stairwell somewhere to flow that wasn't towards the people inside.



The door tipped into the stairwell and came to rest against the opposite wall, resting at a forty-five degree angle, sloping up toward the railing.  The water in the stairwell flowed inside, an unfortunate consequence.  The cape with the Halberd set to using the blur of the Halberd to to cut lines into the back of the door and to remove the railing, so there was sufficient traction for people walking up and out of the door.



I stepped down to investigate, sent a few bugs in to get the lay of the land.  The interior of the shelter was surprisingly like what Coil's headquarters had been like, concrete walls with metal walkways and multiple levels.  There were water coolers and a set of freezers, bathrooms and a sectioned off first aid area.



It was clear that one of the waves or Leviathan's creation of that massive sinkhole in downtown had done some damage to the shelter.  Water was pouring in from a far wall and from the front door, and twenty or so people were in the first aid bay on cots, injured and bloody.  A team of about fifty or sixty people were moving sandbags to reduce the flow of water into the chamber from the cracked back wall.  A second, smaller team was blocking off the room with the cots, piling sandbags in the doorway.  In the main area, people stood nearly waist deep in water.



``Everyone out!'' Laserdream called out.



Relief was clear on people's faces as they began wading en masse toward the front doors.



My dad was taller than average, and I hoped to be able to make him out, see if he was in the crowd.  As the group gravitated toward the doorway, however, I lost the ability to peer over the mass of people.  I didn't see him.



I hung back as people filed out in twos and threes.  Mothers and fathers holding their kids, who otherwise wouldn't be tall enough to stay above water, people still in pajamas or bathrobes, people holding their dogs above water or with cats on their shoulders.  They marched against the flow of water from the stairwell, up the back of the vault door and onto the street.



Mr. Gladly was near the back of the crowd, with a blond woman that was taller than him, holding his hand.  It bugged me, in a way I couldn't explain.  It was like I felt he didn't deserve a girlfriend or wife.  But that wasn't exactly it.  It was like this woman was somone who maybe liked him, heard his side of things, validated his self-perception of being this excellent, `cool' teacher.  A part of me wanted to explain to that woman that he wasn't, that he was the worst sort of teacher, who helped the kids who already had it easy, and dropped the fucking ball when it came to those of us who needed it.



It was surprising how much that chance meeting bugged me.



A shriek startled me out of my contemplations.  It was quickly followed by a dozen other screams of mortal terror.



\emph{Impel deceased, CB-10}.  \emph{Apotheosis deceased,} CB-10.



\emph{ }I felt him arrive, a small few bugs still inside him, though most of the rest had been washed away in his swim.  There were so few I'd missed his approach.



Leviathan.



People ran back inside the shelter, screamed and pushed, trampled one another.  I was forced into the corner by the door as they ran into the shelter, tried to make some distance between themselves and the Endbringer.



\emph{Laserdream down, CB-10}.



And he was there, climbing through the vaultlike door, so large he barely fit.  One claw on either side, he pushed his way through.  Stood as tall as he could inside the front door, looking over the crowd.  Hundreds of people were within, captive, helpless.



A lash of his tail struck down a dozen people in front of him.  The afterimage struck down a dozen more.



No death notice from the armband for civilians.



Leviathan took a step forward, putting me behind him and just to his right.  He lashed his tail again.  Another dozen or two dozen civilians slain.



Mr. Gladly's girlfriend was screaming, burying her face in his shoulder.  Mr. Gladly stared up at Leviathan, wide eyed, his lips pressed together in a line, oddly red faced.



I didn't care.  I should feel bad my teacher was about to die, but all I could think about was how he'd ignored me when Emma and the others had had me cornered.



One hand on my shoulder to steady my throbbing broken arm, I slipped behind Leviathan, hugging the wall, slipping around the corner and moving up the vault door with padded feet.



It was a dark mirror to what Mr. Gladly had done to me.  What Emma and her friends had done, I couldn't say for sure that I would have had the mental fortitude to put up with it if I hadn't gotten my powers – and for all he knew, I hadn't.  I couldn't know whether I could have dealt with everything that had followed the incident in January, if I could have made it this far if I hadn't had my powers, these distractions.  In every way that mattered, Mr. Gladly turning his back on me, back there in the school hallway, a time that felt so long ago, could have killed me.



A fitting justice, maybe, leaving him in that shelter with Leviathan.



I saw Laserdream lying face down in the water, bent down and turned her over with my good hand and one foot, checked she was breathing.



The two capes, who I took to be Impel and Apotheosis, were torn into pieces.  I ran past them.  Ran past the civilians who Leviathan had struck down, ripped apart.



I stopped, when I found the Halberd, picked it up.  Found Impel's armband, bent down and pressed the buttons to open communications, ``Leviathan's at the shelter in CB-10.  Need reinforcements fast.''



Chevalier replied, ``\emph{Shit.  }He must have gone through some storm drain or sewer.  Our best teleporter's dead, but we'll do what we can.''



Which left me only one thing to do.  I had to be better than Mr. Gladly.



I ran past Impel and Apotheosis, passed Laserdream, and reached the shelter's entrance once more.



Leviathan was further inside, crouched, his back to me.  His tail lashed in front of him.  Terrified screams echoed from within.



It was agonizing to do it, but I moved slowly, to minimize the noise I made, even as every second allowed Leviathan more time to tear into the crowd.  To move too fast would alert him, waste any opportunity I had here.  A backwards movement of Leviathan's tail arced through the air, fell atop me, forcing me down into the water.  Gallons of cold water dropping down from ten feet above me.



I swallowed the scream, the grunting of pain that threatened to escape my throat, stood again, slowly.



With only one hand, I didn't have the leverage to really swing the Halberd.  I had to hold it towards the top, near the blade, which meant having less reach, having to get closer.



When I was close enough, I drew the blade back and raked it just below the base of his tail.  Where his asshole would be if he had human anatomy.  Easiest place for me to reach, with him crouched down like he was.



Dust billowed and Leviathan reacted instantly, swiped with one claw, fell onto his side when the damage to his buttocks and the hampered mobility of his tail screwed with his ability to control the movement of his lower body.  His claw swipe went high.  His afterimage was broken up by the the wall above the door, but enough crashed down in front of and on top of me to throw me back out of the shelter, into the toppled shelter door.  I was pushed under the water, the Halberd slipping from my grip.



I climbed to my feet at the same time he did, but I had a clear route up the back of the shelter door while he had to squeeze through the opening.  I was on the street and running well before he was up out of the stairwell.



I gathered my bugs to me, sent some to him, to better track his movements.  As he climbed up, I gathered the swarms into decoys that looked human-ish, sent them all moving in different directions, gathered more around myself to match them in appearance.



With the effects of my slash of the Halberd combined with the damage Armsmaster had already done, Leviathan didn't have the mobility with his tail he otherwise would.  When he attacked my decoys, he did it with slashes of his claw and pouncing leaps that sent out afterimages to crash into them.  A swipe of the claw's echo to disperse one swarm to his left, a lunge to destroy one in front of him.  Another afterimage of a claw swipe sent out to strike at me.



Water crashed into me, hard as concrete, fast as a speeding car.  I felt more pain than I'd ever experienced, more than when Bakuda had used that grenade on me, the one that set my nerve endings on fire with raw pain.  It was brief, somehow more real than what Bakuda had inflicted on me.  Struck me like a lightning flash.



I plunged face first into the water.  My good arm on its own wasn't enough to turn me over – the road just a little too far below me.  I tried to use my legs to help turn myself over.  Zero response.



I'd either been torn in two and couldn't feel the pain yet or, more likely, I'd been paralyzed from the waist down.



\emph{Oh.}



Not like I really should've expected any different.  Neither case was much better than the other, as far as I was concerned.



My breath had been knocked out of me at the impact, but some primal, instinctual part of me had let me hold my breath.  I lay there, face down in two or three feet of water, counting the seconds until I couldn't hold my breath any more, until my body opened my mouth and I heaved in a breath with that same instinctual need for preservation, filled my lungs with water instead.



The lenses of my mask were actually swim goggles, it was a strange recollection to cross my mind.  I'd bought them from a sports supply store, buying the useless chalk dust at the same time.  Durable, high end, meant for underwater cave spelunkers, if I remembered the picture on the packaging right.  Tinted to help filter out bright lights, to avoid being blinded by any fellow swimmer's headlamps.  I'd fitted the lenses from an old pair of glasses inside, sealed them in place with silicon at the edges, so I had 20/20 vision while I had my mask on without having to wear glasses beneath or over it, or contact lenses, which irritated my eyes.  I'd built the armor of my mask around the edges of the goggles so the actual nature of the lenses wasn't immediately apparent, and to hold them firmly in place.



Even so, when I opened my eyes, looked through those lenses for their original purpose, all I could see was mud, grit, silt.  Black and dark brown, with only the faintest traces of light.  It disappointed me on a profound level, knowing that this might be the last thing I ever saw.  Disappointed me more than the idea of dying here, odd as that was.



Through my power, I sensed Leviathan turn, take a step back toward the shelter, stop.  His entire upper body turned so he could peer to his left with his head, turned the opposite way to peer right.  Like a dog sniffing.



He dropped to all fours, ran away, a loping gait, not the lightning fast movement he'd sported when he first attacked.  Still fast enough.



My chest lurched in a sob for air, like a dry heave.  I managed to keep from opening my mouth but the action, the clenching of every muscle above my shoulders, left my throat aching.



Two seconds later, it hit me again harder.



Two blocks away, Leviathan crashed down into the water.



Another lurch of my throat and chest, painful.  My mouth opened, water filled my mouth, and my throat locked up to prevent the inhalation of water.  I spat the water out, forced it out of my mouth, for all the good it would do.



I'd left the fat cape to die like this when the wave was coming.  Was this karma?



Something splashed near me.  A footstep.



I was hauled out of the water.  I felt a lancing pain through my midsection, like a hot iron, gasped, sputtered.  Through the beads of water on my lenses, I couldn't make out much.



Bitch, I realized.  She wasn't looking at me.  Her face was etched deep with pain, fury, fear, sheer viciousness, or some combination of the four.



I followed her gaze, blinked twice.



Her dogs were attacking Leviathan, and Leviathan was attacking back.  He hurled two away, three more leapt in.



How many dogs?



Leviathan pulled away, only for a dog to snag his arm, drag him off balance.  Another latched on to his elbow, while a third and fourth pounced onto his back, tearing into his spine.  More crouched and circled around him, looking for opportunities and places to bite.



He clubbed one away with a crude movement of his tail, used his free claw to grab it by the throat, tear a chunk of flesh away.  The dog perished in a matter of seconds.



Bitch howled, a primal, raw sound that must have hurt her throat as much as it hurt to listen to.  She moved forward, pulling me with her, lifting me up.  When I sagged, she gave me a startled look.



I looked down.  My legs were there, but there was no sensation.  Numb wasn't a complete enough term to explain it.



``Back's broken, I think,'' the words were weak.  The calm tone of the words was eerie, even coming from my own mouth to my own ears.  Disconcertingly out of place with the frenzied, savage tableau.



Leviathan wheeled around, grabbed another dog by one shoulder, dug a claw into the dog's ribcage and cracked  it open, the ribs splaying apart like the wings of some macabre bird, heart and lungs exposed.  The animal dropped dead to the water's surface at Leviathan's feet.



Bitch looked from me to the dog, as if momentarily lost.  In an instant, that look disappeared, replaced by that etching of rage and fury.  She screeched the words, ``Kill him!  Kill!''



It wasn't enough.  The dogs were strong, there were six of them left, even, but Leviathan was more of a monster than all of them put together.



He heaved one dog off the ground, slammed it into another like a club, then hurled it against a wall, where it dropped, limp and broken.



With that same claw, he slashed, tore the upper half of a dog's head off.



``Kill!'' Bitch shrieked.



No use.  One by one, the dogs fell.  Four left, then three.  Two dogs left.  They backed away, wary, each in a different direction.



Bitch clutched me, her arms so tight around my shoulders it hurt.  When I looked up at her, I saw tears in the corners of her eyes as she stared unblinking at the scene.



Scion dropped from the sky.  Golden skinned, golden beard trimmed close, or perhaps it never grew beyond that length.  His hair was longer than mine.  His bodysuit and cape were a plain white, stained with faded marks of old, dirt and blood, a strange juxtaposition to how perfect and unblemished he looked, otherwise.  There was no impact as he landed, no great splash or rumble of the earth.  Leviathan didn't even seem to notice the hero's arrival.



Leviathan struck at one of the remaining dogs with a broad swing of his tail, caught it across the snout.  It dropped, neck snapped.  A short leap and a slash of the claw dispatched the last.



Scion raised one hand, and a ball of yellow-gold light slammed into Leviathan from behind, sent the Endbringer skidding across the length of the street, past Bitch and I.



Leviathan leaped to his feet, reared around, swung his claws at the air ferociously.  Water around him rose, rushed towards Scion, a wave three times as high as Bitch was tall.  Three times as tall as I might be if I could stand.



Scion didn't move or speak.  He walked forward, and ripples extended from his footsteps, soared past us with some strange motive force.  The ripple touched the wave, and the tower of water collapsed before it got halfway to us, dropping straight down.  Liquid as far as the eye could see was being flattened out into a disquieting stillness by the ripples of Scion's footsteps, like a great pane of glass.



Leviathan lunged up to the side of a half-ruined building, leaped down to a point three-quarters of the way between himself and Scion.  His afterimage slammed into the hero.



Scion turned his head, shut his eyes, let the water wash over and past him.  When the attack was over, he squared his head and shoulders, facing Leviathan head on, raised a hand.



Another blast of yellow-gold light, and Leviathan was sent sprawling.



I saw the ripples and waves of Leviathan striking the ground wash past us.  Saw, again, how the ripple of Scion's footstep seemed to wipe out and override that disturbance, returning the water to a perfect flatness.



Leviathan grabbed a car, twisted his entire upper body to toss it in the style of an olympic hammer-throw.  The car hurtled through the air, and Scion batted it aside with the back of one hand.  The vehicle virtually detonated with the impact, falling into a thousand pieces, each piece glowing with golden-yellow light, disintegrating as they splashed into the water.



Scion raised one hand, and there was a brilliant flash, too bright to look through.



When the spots faded from my vision, I saw that one of the damaged buildings was emanating that same light the pieces of the car had, was toppling, tipping towards Leviathan.  Scion, fingertips glowing, started his slow advance as the structure was pulled atop the Endbringer.  The ripples of his footsteps erased any disturbance in the water from the building's collapse



Leviathan heaved himself out of the rubble, turned to run, only for water to rise and freeze solid in one smooth movement, forming a wall as tall as Leviathan was, a hundred feet long.  He paused for a fraction of a second, to gauge which way he might go, poise himself to leap over.  Scion caught him with another golden-yellow blast before he could follow through.



The movement of the water and the creation of the ice hadn't been Scion.  Eidolon approached, flying close, raising one hand to create a ragged mess of icicles where Leviathan was to land.  Some impaled the Endbringer, but by and large, they shattered beneath him, left him scrabbling for traction and footing for long enough that Scion could shoot him again, send him through the barrier of ice as though it were barely there, tumbling.



Scion paused, turning to look at Eidolon, his eyes moving past Bitch and me like we weren't even there.  His eyes settled on the hero, the most powerful individual in the world staring at the man who was arguably the fifth.



His expression was so hard to read.  I knew, now, what people had meant, when they said they thought his face was a mask, a facade.  Though it was expressionless, though there was nothing I could point to to explain why I felt the way I did, somehow I sensed disgust from him.  Like nobility looking at dog shit.



Scion turned away from Eidolon to focus on the enemy once more.  He blasted the Endbringer again.  Floated up and moved past Bitch and me faster than I could see, to strike the Endbringer a fraction of a second after the blast of light struck, stopping there in midair to blast Leviathan a second time as the Endbringer was still flying through the air at the punch's impact.  Everything about Scion and his actions was utterly silent. His movements or attacks didn't even stir the air.  Only the effects, Leviathan striking the water, the breaking of ice, generated any movement, shudders or sounds.



Eidolon froze the water around Leviathan's four claws, giving Scion the opportunity to land another blast.  Leviathan turned, raised a spraying wall of water to cover his retreat.  Scion sent out one blast of his golden light to strike the wave, following up with a second blast before the first even made contact with the water.



Seeing the second blast coming, Leviathan leaped to one side.  No use – the blast of light curved in the air to head unerringly for him, struck him down.  Edges of the Endbringer's wounds glowed golden yellow, drifted away into the air like flecks of burning paper caught in the updraft of hot air.  A fist imprint near the base of Leviathan's throat glowed with edges of the same light, the wound continuing to spread and burn as I watched.



A tidal wave appeared in the distance, at the furthest end of the street, near the horizon.



Scion sent out a blast of golden light the size of a small van, darting to the center of the wave, disappearing into a speck of light before it made contact with the distant target.  The middle third of the wave buckled, fell harmlessly into a splash of water, all momentum ceased.  The other two sides of the wave curved inward, bent, to bear unerringly towards us.



Another blast of golden light, and one side was stopped, stalled.  A third blast was spared for Leviathan, who was getting his hands and feet firmly on the ground, crouching in preparation to run.  The Endbringer was knocked squarely to the ground.



Scion stopped the third wave in its tracks with a fourth blast, but the water was still there, and it still bowed to gravity.  The water level around us rose by a dozen feet, momentarily, slopping as gently over us as physically possible, like a lap of water on the beach.



When the flow of water was past us, I could see a fifth blast of light following Leviathan, who had used the cresting water to swim away.  He was making his way to the coast.  Scion rose, flew after his target with a streak of golden light tracing his movement.  Eidolon followed soon after.



Ten, fifteen seconds passed, Bitch holding me, averting her eyes from the corpses of her dogs, jaw set, not speaking or moving.



A teleporter appeared beside Laserdream, a distance away.  He looked at us, startled, glanced at his armband.



``You okay?'' he called out.



``No,'' I tried to shout back, but my voice was weak.  Bitch spoke for me, ``She needs help.''



``Bring her here, I'll take her back.''



Bitch carried me, dragging me by my collar to where Laserdream lay.  I grunted and groaned in pain, felt those hot pokers through my upper back and middle, but she wasn't the type for sympathy or gentleness.



The teleporter touched one hand to my chest, another to Laserdream, who turned her head to look at me.



There was a rush of cool air, and we were in the midst of chaos.  Nurses, doctors, moving all around us.  I was lifted and placed on a stretcher, hauled up by four people in white.  There were shouts, countless electronic beeps, screams of pain.



I was placed on a bed.  I would have writhed with the pain of being shifted if it weren't for my general inability to move.  There was a heart monitor on one side, a metal rack with an IV bag of clear fluid on the other, thick metal poles beside each, stretching from floor to ceiling.  Curtains loomed on either side of me, making for a small room, ten feet by ten feet across. The emergency room, triage or whatever was in front of me, past the foot of the bed, a dozen more cots, doctors doing what they could for the massed injured, civilian and cape alike.



All around me, nurses moved with a rote efficiency, to put a clip on my finger, and the heart monitor started beeping in time with my own heartbeat.  One put some sticky glue on my collarbone, pressing an electrode down there.



``My back, I think it's broken,'' I said, to no one in particular.  Nobody in particular replied.  All of them too busy with set tasks.  People seemed to approach my bedside and leave to go attend to another patient elsewhere.



``Your name?'' someone asked.



I looked to the other side of me.  It was an older woman in a nurse's uniform, pear shaped, gray haired.  A man in a PRT uniform stood behind her, holding a gun on me.



``Skitter,'' I replied, confused, feeling more scared by the second.  ``Please.  I think my back's broken.''



``Villain?''



I shook my head.  ``What?''



``Are you a villain?''



``It's complicated. My back-''



``Yes or no?'' the Nurse asked me, stern.



``Listen, my friend, Tattletale, do you know-''



``She's a villain,'' the PRT uniform cut me off, touching his way through some blackberry device with his free hand.  ``Designation Master-5, specifically arthropodovoyance, arthropodokinesis.  No super strength.''



The nurse nodded, ``Thank you.  Handle it?''



The man in a PRT uniform holstered his gun and stepped up to the bed.  He grabbed my right wrist, clasped a heavy manacle around it, fixed it to a vertical metal pole by the head of the bed.



``My other arm's broken, please don't move it,'' I pleaded.



He gripped it anyways, and I couldn't help but scream, strangled, as he pulled it to one side, clasped a manacle down on my wrist, hooked the other side of the manacle to the second pole.



``What-'' I started to ask a nurse, as I forced myself to catch my breath, stopped as she turned her back to me and pulled the curtain closed at the foot of the bed, walked past it.



``Please-'' I tried again, looking to the PRT uniform, but he was pushing his way past the curtain, leaving my company.



Leaving me chained up.  Alone.





