All of the adrenaline, emotions and endorphins that had been building since I first heard the sirens, maybe even before them – when I learned about Dinah Alcott – made for one hell of a rush.  More relevant to the present, it made for one hell of a mental wipeout as I came down from the rush.  A low point to equal the `high'.



The background noise of screams, shouted orders of doctors and nurses, a hundred heart monitors beeping out of sync and my `cell' of three curtained `walls' cutting me off from everything else?   Didn't help.



My arm hurt, and hanging from the manacle made that ten times as bad.  My back was the worst thing, a slow, steady, pain that terminated in my midsection. It seemed to build in intensity every second I paid attention to it, settling into a dull blistering of pain when I focused my attention elsewhere.  If I didn't focus on keeping my breathing steady and deep, I found that I unconsciously held my breath to minimize the pain.  That only made it worse when I did have to breathe again, because it brought tightness in my throat and chest, along with agonizing coughing fits.



None of that was even touching on that growing terror over the fact that, hey, I couldn't feel my legs, and it wasn't getting better.



If my back was really broken, it could mean my best case scenario was surgery and years of physical therapy, years of crutches and wheelchairs.  My worst case scenario would be never walking again.  I didn't have a power that would help too much on that front.  It would mean the end of my career as a cape, never having sex with a boy the natural way, and never going for another morning run.



I made myself take a deep breath.  It shuddered as I exhaled slowly, and not just because it hurt to breathe.



I couldn't do anything about my back, in the here and now.  My arm?  Maybe.  The metal pole was fixed to the wall at every foot or so by horizontal bars, and the end of the manacle was stopped from descending any further by one of the bits that extended to the wall, three feet or so above my head.



I couldn't really believe they were going to arrest me.  Like Tattletale had said, there were rules.  Largely unspoken rules, but still more important than anything else in the cape community.  You didn't profit from an Endbringer attack, you didn't attack your nemeses or take advantage of undefended areas to steal.  You didn't arrest a villain that came to help.



Because when people started doing that, the truce broke and things became ten times easier for the Endbringer.



The manacle on my wrist made me wonder.  I'd made some enemies with the good guys.  Maybe I was getting some rough treatment because of it.



One ominous idea nagged at me, and I couldn't get it out of my head.  It was that I might not get any treatment at all – for my back, specifically – because of grudges against me and capes who could `suggest' that maybe the doctors' resources could be better directed elsewhere.



If they went that route, one hundred percent deniable, excusable, then there'd be nothing I could do about it.



If that was what was going on, being manacled like this would be something of a slap in the face, a way of letting me know it was intentional, while keeping me from contacting anyone to complain.



My arm shifted involuntarily as I cringed at a painful intake of breath, swinging a little, and I clenched my teeth.



I turned my head, gripped the fabric of my pillow with my teeth, tugged and pulled my head forward at the same time.  It moved to my left.  I did it again, bumped my shoulder, making my arm swing on the chain once more.  I suppressed the noise I might've made at the pain, choked back the gorge that rose in my throat.



Whatever was going on with my back, it prevented me from sitting up, denied me the use of my abdominal muscles.  I could only work with my shoulders, my head, my teeth.



Shifting the pillow over several long minutes, I managed to gingerly ease it under my shoulder and upper arm.  Provided I didn't move -which I couldn't, really- it gave my arm something to rest on, prevented all of the weight from dangling off of my cuffed wrist.



Of course, I was now absent one pillow for my head and neck, and the propped up shoulder and arm made my back twist slightly, which only intensified the pain there.  I closed my eyes, focused on just breathing, tried not to pay too much attention to how slowly time was passing by, or the cacophony of noise from the rest of the triage area.



I hated this.  Hated not knowing, not having any information about what had just happened, what was happening, what was \emph{going} to happen.



Roughly half of my nightmares about being bullied took place in the classroom, knowing that a class was just about to end, or that a teacher was about to assign us group work.  That some group of faceless bullies were waiting to pull the worst `prank' yet.  It was the idea that I was about to be put in a situation where something bad was about to happen, that it was inevitable.  Being helpless to do anything about it.



Maybe it was stupid, but I'd never failed to wake up drenched in sweat after that, even when I woke up before the follow-through.  The dreams had come less often after I got my powers, but they still came from time to time.  I had suspicions they might come even years after I left high school behind me for good.



But that state of mind in the nightmares?  I felt like that now.  Trying to keep from panicking, knowing that no matter what I did, I was counting on luck and forces beyond my control to not ruin my day, my week, my month.  Ruin my life.



I'd done the heroic thing.  Drawn Leviathan away from those in the shelter who were still alive.  A part of me was proud of myself.  The rest of me?  Faced with the idea of spending the rest of my life in a wheelchair?  I felt like an idiot of epic proportions.  I'd bought into the idea of the grand, noble gesture, and in the here and now it felt like I had to convince myself that what I had done mattered.  It sure as shit didn't seem to matter to anyone else.



The chain of my manacle clinked taut as I yanked my right hand forward angrily.  The pain that caused me in my midsection stopped me from doing it again.



A girl in a nurse's uniform pushed the curtain aside to enter.  I identified her as a \emph{girl} rather than a woman because she barely looked older than me.  Bigger in the chest, for sure, but baby faced, petite.  Her brown hair was in a braid, and the lashes of her downcast eyes were long as she stepped to the foot of my bed, picked up a clipboard.  She was very carefully not looking my way.



``Hi,'' I spoke.



She ignored me, turned her attention to the heart monitor, made a note on the clipboard.



``Please talk to me,'' I spoke.  ``I have no idea what's going on, and I feel like I'm losing my mind, here.''



She glanced at me, looked away hurriedly the same reflexive way you'd pull away from a hot stove with your hand.



``Please?  I'm-  I'm pretty scared right now.''



Nothing.  She took more notes on the clipboard, noting stuff from the screen the electrode ran to.



``I know you think I'm bad, a villain, but I'm a person, too.''



She glanced at me again, looked away, returned her eyes to the clipboard and frowned.  She stopped writing as she glanced up to the monitor, as if she had to find her place or double check her numbers.



``I have a dad.  Love him to death, even if we haven't talked lately.  I love reading, my- my mom taught me to love books from the time I was little.  My best friend, it wasn't so long ago that she helped pull me out of a dark place.  I haven't heard how she's doing.  If she's dead or if she's here too.  Have you seen her?  Her name's Tattletale.''



``We aren't supposed to talk to the patients.''



``Why not?''



``While back, some cape sued the rescue workers after a battle much like this.  Hadhayosh, I think.''



``That's one of the other names for Behemoth.  Like Ziz is for the Simurgh?''



``Yes, some heroes got hurt badly enough they wouldn't recover, they knew they had no more income from their costume career, so suing, it was a way--'' she stopped, closed her mouth deliberately, as if reminding herself to stay silent.



``You can't tell me if my back's broken or not?''



She shook her head, ``No.''



``I won't tell.  I won't sue.''



``Saying that isn't legally binding,'' she frowned, again, ``and It- it's not that.  I'm just a nursing student.  I haven't even graduated.  They recruited us to help meet demand, to do the paperwork and check that patients weren't coding, so the people with experience could focus on handling the patient load.  I don't have the training to diagnose you on any level, let alone your back.''



My heart sank.  ``Have you seen Tattletale?  Have you heard if she's dead or injured?  She wears a lavender and black costume, and there's this eye in dark gray on the black part across her chest--''



``I'm sorry,'' she hurried to the foot of the bed, hung up the clipboard.



\emph{I'm sorry?  }Was that an answer – condolences – or was it a refusal to speak on the subject?



I might have made a noise, because she turned back, stopped.  I couldn't be sure, though, over the sounds from the other nurses, doctors and patients.



``We've got a code!'' someone screamed, just beyond the curtain.  ``Need paddles!''



``Paddles are in use!''



``Then get me someone with electricity powers!  And you, resuscitate!''



I closed my eyes, tried to stop myself from imagining that they were talking about Tattletale, or my dad, or even Brian, though I was pretty sure Brian had made it out okay.  Even as I managed to dismiss those images from my mind, a voice in the back of my head noted that whoever was on the table was important to \emph{somebody}.  So many beloved family members, friends, coworkers, gone from people's lives.



``Do you want to call your dad?  Or try calling your friend?'' the nurse-in-training offered me.



If she was offering for me to call Tattletale, that at least meant she hadn't seen Tattletale's body.  That was some relief.



I wasn't sure if I should take the offer.  If I called my dad, would they track the call?  Find out who I was?  Would they track down Tattletale, if she wasn't dead or dying?  Who else could I call?  Coil?  Way too many issues if they traced the call, and I wasn't sure if Lisa had passed on word of our recent argument and/or breakup.  Grue, Regent, Bitch?  I wasn't on their team anymore.



A darker thought struck me.



``Is that – would that be my one phone call?  These cuffs – am I being arrested?''



She shook her head, ``I was just offering.  I don't know if they're arresting you.  Only thing they said was that I was supposed to fill in the charts for the patients on this end of the room that have the red tags.''



She pointed to a set of plastic tags that were clipped to the curtain rod, so that one large tag hung down on either side of it.  Was it to designate the seriousness of my injuries?  No, they hadn't even examined me.



I drew a connection to my line of thinking from earlier – was it because I was a villain?  Did I get a mere check-in from the nurse-in-training while the heroes got actual nurses and doctors?  I hadn't seen anyone put the tags up, but then again, I hadn't been looking at the curtain rod right after I was stuck here.



``Okay,'' I spoke, quiet, my thoughts going a mile a minute.



``The phone call, I can let you use my cell phone if you promise not to\ldots'' she trailed off, as if realizing the possibilities of what could happen if a villain had her phone number, contact info for her friends and family.  Yet she could hardly back out, not without potentially upsetting a bad guy.



I shook my head.  ``No.  But it's really good of you to offer.  Thank you,'' I tried to put as much emphasis on the thanks as possible.  ``With that kind of empathy, I'm sure you'll become a great nurse.''



She gave me a funny look, then backed out through the curtain.  I could have called after her, asked for something for the pain, asked if maybe I could get some help, but I suspected she didn't have the power to give me any of that.  I had no idea how long I'd be here, and I suspected it'd be worth more to have a potential friendly face around than go for the long shot and risk seeming manipulative or alienating her.  That, and I didn't want to get her in trouble.



Minutes ticked on.  No more than three seconds passed without someone screaming or shouting orders or updates regarding a patient in crisis.  It would have been interesting to listen to, if I could make out more than half of it, and if the half I could hear wasn't so horrible.



The anxiety over my circumstances and not knowing what was going to happen was gradually overridden by a maddening boredom.   I couldn't move, had nobody to talk to, didn't know enough about my present situation to think up contingency plans.



I closed my eyes and used my power, because it let me be outside my own body in a way, because it was \emph{something} to do.



A handful of cockroaches from near the kitchen made their way through the walls, through an air intake grate in the wall, and up to my bed.  They gathered on my stomach.



I gathered them into a pyramid on my stomach, let them collapse.  Made a kaleidoscopic starburst pattern, then moved them all in sync to expand out into a perfect circle.



``You're so creepy, you know that?'' the voice was familiar, but I couldn't place it.



``I've heard worse,'' I replied, opening my eyes.  Panacea was entering my curtained enclosure, shutting the curtain behind her.  There was a PRT uniform with her.



``I'm sure you have,'' she frowned.  Her hood and scarf were down, so I could see her face, much as I had during the bank robbery.  She had dark circles under her eyes that looked painted on.  She spoke, sighing the words, ``I need your permission to touch you.''



``What?''



``Liability reasons.  Someone overheard you say you've got a broken back.  There could be other complications, and that takes people, time, equipment and money that the people in charge of this hospital are reluctant to spare at a time like this.  You could refuse to let me touch you, make the hospital give you the X-rays and MRI, get months or years of treatment paid for by the Preservation Act, all under oppressive confidentiality agreements that could cost the hospital millions.  It's an option, but the treatment wouldn't be as fast, good or effective as it would if I used my power.  You'd be shooting yourself in the foot for the sake of being stubborn.''



``Um.''



``Just agree, so I can move on to other patients.''



``What was it you said during the bank robbery?  You'd make me horribly obese?  Make everything I eat taste like bile?  What's to stop you from doing something like that here?''



``Nothing, really.  I mean, you could sue me after I did it, but you'd have to prove it beyond a reasonable doubt, and that'd be damn hard if I gave the symptoms a time delay before they showed up.  Plus I'm a valuable enough resource that I could get help paying the legal costs.  \emph{And}, let's not forget, Carol, my adoptive mother, is a pretty kickass lawyer.  Whatever you did by trying to sue me probably wouldn't cripple me as much as what my power did to you.''



``That's not reassuring.''



``It's not meant to be reassuring.  I suppose maybe you'll just have to either trust in the fact that I'm a decent person or refuse my help,'' she shrugged, glaring at me, ``There's a kind of poetry to this.  Like, a thief fears being stolen from the most, a scumbag\ldots well, you get the drift.  The more horrible a human being you are, the more you'll agonize over what I might have done to you, with a time delay of minutes, hours, days, \emph{years}.  Yet if you're a decent person, you'll be more inclined to think better of me.''



``Are you?''



``What?''



``\emph{Are} you a decent person, Amy?''



She gave me an offended look.



``I envy you, that it's so easy for you to think of things in terms of black and white.  I'd like to think I'm a good person, believe it or not.  Everything I've done, I did because I thought it was right at the time.  In hindsight, some of the ends didn't justify the means, and sometimes there were unforseen consequences.''  \emph{Like Dinah.}  ``But I don't think of myself as a \emph{bad} person.''



``Then you're either ignorant, deluded or you have a very twisted perspective.''



``Maybe.''



She went on, ``Don't really care which it is.  If you're going to call yourself a good person,'' she paused, shook her head a little, ``Then don't waste my time.  Give me an answer, one way or another, so I can get on with helping people.''



It wasn't really a choice.  A long, hard road to recovery, possibly with no recovery at all, fraught with any potential health complications that the universe decided to hand my way, or healing for a broken back, with the potential health complications that Panacea decided to give me?



I mean, whatever she deigned to inflict on me would be calculated to make me miserable, if she went that far, but at least then I'd have someone to \emph{hate}.



``Please,'' I spoke, ``Use your power.''



She nodded at the PRT uniform, who left the enclosure.  Then she approached the side of the bed.



``I'm going to have to move some of your mask aside, to touch your skin.''



``Permission granted,'' I spoke, ``Though I've been wondering since the bank robbery – why didn't you reach up and touch my scalp?''



``No comment.''



\emph{Ah}.  Something about hair, maybe?  A weakness in her power.  Maybe it was mucked up or confused by `dead' tissue?



She fumbled with my mask for a second.



``Lower,'' I informed her, ``The mask and body part of the costume overlap just above the collarbone.''



She found it, separated the two, and touched a fingertip to my throat, like she was taking my pulse.



The pain left in an instant.  My breathing became easier, and I felt a steady pressure deep in my broken arm.



``You have a brain injury that's not fully healed.''



``Bakuda's fault.''



``Hm.  Outside the scope of my abilities.''



Ominous, but I wasn't ready to put too much stake in what she told me, and what she might be leaving out.



``Okay,'' my voice was stronger, without the crippling pressure in my chest and back.



``Microfracture in your shoulder, nerve damage to your left hand, reduced fine dexterity.''



``Really?  I hadn't noticed.''



``It's there.  I'm not going to bother with that, either.''



``Wasn't expecting you to.''  Couldn't let her ruffle me.



``Broken arm, broken spine, fractured ribs, small perforations in colon, kidney and liver, some internal bleeding.  This will take a minute.''



I nodded.  It was more severe than I'd thought.  That unsettled me some.



A part of me wanted to apologize for what had happened at the bank robbery, but the tone of our earlier conversation made it feel like I'd be trying to dissuade her from doing something malicious with her power.



Relief overwhelmed me as sensations began returning to my legs.  They were quick, like being shocked, but they ranged from hot to cold to the unfamiliar, running from my abdomen to the tips of my toes, tracing every internal area of my legs.



``Ow,'' I muttered, as one line of pain drew itself from my hip to my ankle.



``I've got to test your nerves as I re-establish the connections, but I'm too tired to do it all with my power, and I can't dope you up with endorphins because Armsmaster, Miss Militia and Legend will be coming to talk to you in a bit, and I've been told you need your head one hundred percent clear for that.  So some of this is going to hurt.''



``Wait, what?  Why do I need my head clear to talk to them?  Why are they talking to me?''



``Mmm.  I can feel your emotions in your body, hormones and altered chemical balances.  You're scared.''



``Damn right, I'm scared – ouch.  Fuck, that stung.''  My leg jerked.



``It's going to happen any time my concentration slips.  Best to stay quiet.''



``No, seriously.  Why are they talking to me?  Is that why I'm in handcuffs?  To keep me here until they, what, arrest me?''



``No comment,'' she smiled a little.



``Hey, no.  You can't call yourself a decent person and then leave me here agonizing over details.''



``I can.  I don't know what they want to talk to you about, though I have\ldots strong suspicions,'' her eye drifted to my manacle.  ``But I have been informed that you are to be lucid and fully mobile.''



``Why?''  I had a growing suspicion as to why, helped by her glance to my restraints.  If they were arresting me, they couldn't have me agree to any deals or plea bargains while I was drugged up, or it would be thrown out of court.  I was pretty sure.  One semester of a law class didn't exactly leave me an expert.



``According to the woman from the PRT that I talked to, it will work best if all of you are kept in the dark for as long as possible.''



\emph{``All of us?''}  It wasn't just me.



``A slip of the tongue.'' She smiled slightly, as if enjoying stringing me along.



``Do these others include Tattletale?'' I asked, ``Did you heal her?''



She quirked an eyebrow.  ``No.  I can tell you I didn't.''



``You didn't.  Because she didn't need your help, or because she was already dead?  Ow!''



My leg jerked again, a muscle in my thigh clenching hard, not unlike a charlie horse.  It subsided.



``I think we're done here.''



``Hey!'' I raised my voice again, ``Give me an answer!  Stop fucking with me!''



She lifted her finger from my throat, and many of my smaller bruises and scrapes began making themselves felt once more.  I could breathe without a problem.  I wiggled my toes experimentally, felt them move against the soles of my costume.  I moved my left arm, felt no pain.  Tugged on the chain with it and felt everything working as it should, no pain.



She leaned close, so her mouth was by my ear, ``Not so fun, is it?  Let me tell you, this isn't a hundredth of the mind-fuckery that your teammate was pulling on me, back then.''



``That wasn't--'' I stopped.



``What?  Wasn't you?  You stood by and watched it happen, played along, took advantage of it.  Or maybe you were going to say it wasn't that bad?  You \emph{really} don't know.  You don't know me, you don't know Glory Girl, you don't know what Tattletale was saying, how she was threatening to ruin my life.  Imagine the person you care about most, finding our your darkest secrets.  Secrets that, even if they eventually came to accept it, you know they would taint and color every single conversation you have with them afterward.''



I couldn't help but picture it.  My dad finding out I was a villain, what I'd done.  Forevermore having doubts about me.



``I'm sorry,'' I spoke, my voice low.



``Maybe you are.  I doubt it.  I'm sorry to leave you wondering what happened to your teammate, what the big name capes are going to say to you, but I have others to help.''



She didn't sound sorry at all.



``Hey!''  I raised my voice again, ``Come back here!''



She turned her head to give me a dark look as she walked away, ``Good luck with Armsmaster.''



I pulled on the chains, angrily.  I almost, \emph{almost} sent the cockroaches on the bed after her.  I stopped when I saw the PRT uniform hold the curtain back for her in courtesy.



When Armsmaster and Legend arrived, it would be too late.



I sent the roaches after \emph{him}, the PRT uniform.  They landed on him, individually squeezed into the pouches on his belt and bandoleer.



Found the keys on his belt.



Getting the keys out of the pouch was harder.  I had to be smooth, and the keychain was heavy enough that the roaches couldn't pick it up with their mouths.  Instead, I tried lifting it up with the middle of a roach's body, supported by the rest.  No luck, it slipped free off of the convex exterior of the cockroach's shell.



I turned it upside down, instead, used the more textured underside to catch the loop of metal.  The rest of the roaches latched on, hauled the roach up and out of the pouch, squeezed it through the flap-covered opening, breaking it nearly in two against the metal of the ring as they drove it through the too-narrow gap.  One roach dead, but the keys were falling free of the pouch.



Instinct took over, and I unconsciously bid roaches to move into place beneath the keys as they fell to the floor, muting  the noise of metal against the ground.  They skittered my way, the weight of the keychain managed between them.



Hopefully people were too busy to notice the falling keys or the small number of bugs.  I suspected it was crowded and busy out there, from what I had glimpsed when I was brought in.  If people \emph{did} notice, well, I was still getting arrested anyways, right?



Getting the keys up onto the bed would be harder.  I had the roaches put the keys beneath the bed, set them on the blanket, to start unraveling it.  Ten sets of mandibles -eleven now, as another cockroach came from the air vent- each working at individual threads.



I was torn between rushing this and doing it right.  I had to convince myself that I wouldn't be dragged off to jail in the next five or ten minutes.  Probably.



It probably took that long to get a long enough piece of thread.  One group of bugs set to looping the thread around the keychain, tying it into a firm knot, while the others brought it up the side of the bed, up my body, my arm, and to my hand.  Once I had the thread in my fingers, I started winding it up around my fingers with a circular motion of my hands, reeling in the keys.



In a matter of seconds, I had the keys in hand.  Good.



The cockroach that had brought me the thread helped me figure out the keys that would work, traveling over them to eliminate the ones that were too large, acting as an added digit to help sort through them and putting the right keys between my fingers.  It guided the end of the keys into the lock.  The first key didn't fit, too large.



The second unlocked the cuff.



I hurried to unlock the cuff on my left hand, flexed my hand and arm, rubbed at my wrists.



I pulled the covers off, swung my legs over the side of the bed, and gingerly tested them against the ground.  They supported my weight.



The relief was palpable.  Almost something I could feel, making me want to hug my arms around my body in quiet joy.



But my priority was getting out of here.  Not so easy, with the amount of capes and PRT personnel around.  No windows around me, but if I stepped outside the curtain and into the main area, I risked running into someone like Legend or Armsmaster.  I was assuming from what Panacea had said that they had been treated for the injuries that had taken them out of the fight and were up and about.



No, a better plan of action would be to keep out of sight.



I sent my bugs forward, tracing the lines of the curtains and wall.  Once I was sure that the curtains in the next few patient enclosures were closed, I moved the curtain to my right and headed that way.



Some cape I didn't know was unconscious, blood smeared around his nose and mouth, almost caking the upper half of his mask to his face.



Another enclosure, an empty cot, with red stains on the sheets from whatever patient had been there earlier.



There was a window past the next enclosure.  I wasn't sure if I could climb out, or if there would be somewhere to go once I had, but it gave me hope.



I pushed my way into the next curtained enclosure.  Stopped.



\emph{Oh}.



There were shouts behind me, which might have been someone noting my absence.  I was at the point of not caring anymore.



I tried to take a step forward, to move to the bedside or around it, but my newly healed legs gave out under me.  I crumpled into a kneeling position.



Staring up at the occupant of the bed, a few things came to me.  For one thing, I got to experience first hand what Brian had told me, about how he'd gone cold, still and quiet inside on that day he'd gotten his powers.



For another, I realized why they'd had me chained up.  Kind of stupid not to, in retrospect.  A glance at the curtain showed a blue tag, the same style as the red one that had been on my curtain, plastic, unlabeled.



The bed's occupant lay on her back, tubes running into her nose and mouth, an IV in her arm.  An ugly cut marred her right breast and shoulder, which were bare.  Smaller cuts covered the rest of her body.



Running footsteps and the sound of a curtain being heaved open in a neighboring section didn't stir me from my daze.



The bed's occupant wore Shadow Stalker's costume, sans mask.



I recognized her.  Sophia Hess.





