





\emph{Sophia Hess was Shadow Stalker. }



I tried to pull all the individual pieces and clues together, fill in the blanks.  Did this mean Emma was a cape, too?  No – I'd seen Emma in the presence of other capes.  At those times, I knew, she'd have reason to be in costume if she had powers.



But those times I was thinking of, when my cape and civilian lives had crossed?  Emma had been at the mall, where Shadow Stalker had been on duty.  She'd been at the fundraiser, too.  As Shadow Stalker's plus one?  Emma's dad had been there as well.  Was that a clue?



A sick feeling in my gut told me that Emma knew about Sophia and Shadow Stalker.



I could even guess that Emma had found out sometime before high school started, while I was at nature camp.  It would have been an exciting revelation, a juicy secret, being a part of the cape community.  Seduced by that drama, Emma would have turned her back on me, became Sophia's best friend.  The civilian sidekick and confidante to the young heroine; it was cliche, but cliches had their basis in something.



I was probably wrong on some level, but it gave answer to questions I'd assumed I'd never get an answer to.



A  hand seized me by the back of the neck, hauled me to my feet.



Numb, I wobbled, relying heavily on the painfully hard grip to stay balanced.  He turned me around, and I saw Armsmaster, his lips curled in a silent snarl of anger.   A glance at his shoulder showed no sign of the ragged mess from when I'd last seen him, but there was no arm either.  I thought I saw a glimpse of a flat expanse of skin.  Panacea's work?



``\emph{What} are you doing here?!'' he roared the words to my face.



When I couldn't formulate an answer for him, he marched me out of the curtained enclosure, kicking the curtain so it slid shut, moved me towards the nurse's station where Miss Militia and Legend were talking.



I apparently didn't move fast enough for him, because he swung his arm forward, forcing me to stumble forward to keep my feet under me.



It was looking increasingly likely that I would get arrested, but my thoughts turned to the trio, and \emph{their} crime and punishment.  Had Sophia, Emma and Madison had gotten off easy because Sophia was a superhero?  I had my suspicions that the schools worked alongside the Wards, things wouldn't work if they didn't, and the schools were a government institution just like the Wards were.  Did Sophia get easier treatment?  Two weeks suspension when she deserved expulsion?



Had my teachers been looking me in the eye while calculating ways to make things easier on their resident superhero?



Maybe.  More likely that it was some combination of ineptitude, laziness and ignorance, on top of being influenced by the school's link to the Wards program.



Armsmaster slammed my upper body down against the counter of the nurse's station, hard.  I grunted, as much in reaction to being brought back to reality as in reaction to the blow.



``Armsmaster!'' Legend's tone was a rebuke to Armsmaster for the show of force.



More able to take it in stride than the leader of the Protectorate, Miss Militia asked, ``What happened?''



``Escaped her cautionary restraints, caught her peeping on one of the blue tags.''



``Damn it,'' Legend muttered.



``Who?'' Miss Militia asked, ``And how bad?''



``Shadow Stalker.  Saw her unmasked.''



``I see,'' Miss Militia spoke, ``Nurse?  Would you see that everyone without clearance is put to work elsewhere, while we resolve this?''



``Yes ma'am,'' the reply came from a man I couldn't see.



I struggled to turn over, failed.  When I found I couldn't budge Armsmaster's grip, I gave up, slumped onto the counter.



``Who is she?'' Legend asked.



``Skitter, member of the Undersiders, a group of teenage villains,'' Miss Militia replied.  ``Master-5, bugs only.''



``This situation is serious,'' Legend spoke, walking around the counter until I could see him.  I saw nurses and others behind him staring, some of them being ushered away by an older nurse in scrubs.  ``Do you understand?''



He nodded at Armsmaster, and Armsmaster eased his grip some, as if it would make it easier to talk.



I was opening my mouth to speak when the thought struck me – If Sophia was Shadow Stalker, did she know who I was?  She'd heard me talk in costume, hadn't she?  I knew from the time the trio had overheard me in the bathroom and doused me in juice, that at least one of the girls could recognize my voice.



I shook my head a little, as if it could get my thoughts back on track.  ``Nobody explained anything.  You guys were going to arrest me, so I thought I'd leave.''



``Hospital personnel aren't permitted to talk to patients, liability reasons,'' Miss Militia told me, echoing what I'd heard earlier.



``Figured as much when the nurse didn't answer my questions,'' I muttered.  No use dragging that nurse-in-training down with me.  She'd been nice.  ``But Panacea did have words with me when she was putting me back together, and-''



``Panacea is a member of New Wave,'' Armsmaster spoke, and I got the impression the explanation or excuse was meant more for Legend than it was for me, ``She's not official.''



``She's the only person who would talk to me!'' I raised my voice.



``I would ask you to keep your voice down,'' Legend spoke, his voice hard, ``There's very few ways a situation like this can go, with a cape's civilian identity at stake.  If you start shouting, specifically shouting \emph{what you know}, it would \emph{severely} curtail what options you have left to you.  Understand?''



When I didn't come up with a response right away, he added, ``If the tables were turned, if it was you who had your identity uncovered, you would want us taking the same firm hand, giving you that same respect.''



I couldn't help but chuckle silently for a second there.  The armor of my mask clacked against the countertop as I let my head rest there.  Respect?  For Sophia?



Besides, I had suspicions that if the tables were turned, Shadow Stalker wouldn't be pinned against the counter of the nurse's station.



Taking a deep breath – no use digging myself in deeper – I asked, ``You were talking options.  What are they?''



``If you were judged to have used an Endbringer situation to your advantage, you would meet the most serious penalty we can offer.  Those who violate the Endbringer truce are almost always sent to the Birdcage,'' he let that last word hang in the air.



I had to keep myself from laughing again.  This shit was too ridiculous.  This was \emph{Sophia.  }She was five times the villain I was.  The only difference between us were the labels that we stuck on ourselves.  I told him, ``It was an accident.''



``Okay,'' Legend told me.



Armsmaster told him, ``Skitter here has been building a fairly strong reputation as an adept liar, so be cautious.''



``Oh?''



``She's fooled my instincts and my hardware on more than one occasion.''



``Well, I suppose I'll have to keep that in mind.''  When Legend returned his attention to me, his lips were creased in a frown.



What could I say to defend myself now?  Anything I said would be colored by Armsmaster's undeserved comment on my personality.



``Another option would be for you to join the Wards.  We were willing to offer you this when we got around to talking to you, before seeing you on your way.  You would be placed under varying degrees of probation based on your past crimes, but you would earn a paycheck, you'd have a career-''



``No.'' The word left my mouth before I even thought about it.



And when I \emph{did} think about it?  No.  Not with Sophia there.  No way, no how.  If I stepped on her turf, I suspected one of us would kill the other.  Besides, there wasn't one thing about joining the Wards that was even remotely redeeming.



``No?'' he sounded surprised.



``Just\ldots no.  I'd sooner go to the Birdcage.''  I was surprised that I actually meant it.  My contempt for the heroes was growing.  Armsmaster had refused to cooperate with me on any level.  Glory Girl and Panacea hadn't done anything to earn my respect when I ran into them.  Topping it off, they had a personality like Sophia's on their team?  I couldn't even imagine joining them, now.



``I don't think you understand what you're saying,'' Legend spoke as if choosing his words carefully.



I took a deep breath.  ``Is there a third option?''



``You do \emph{not} get to negotiate!'' Armsmaster roared.  Heads turned.



Feeling a flare of anger, I retorted, ``So he gets to yell, but I don't?''



``\emph{We} have the authority here!'' Armsmaster shouted.



``The only authority you have is the authority people give you.''  It wasn't me who responded.  The voice was male, familiar.



``Grue!'' I called out.



``You're alive,'' Grue responded.  ``We thought-''



``Is she okay?  Tattletale!?''



``I'm at about ninety percent,'' Tattletale's voice informed me.  ``\emph{You're} the one that gave us a scare.''



I sagged in relief.



``I would ask you to step back and let us handle this,'' Miss Militia told him.  ``If any of you \emph{do} decide to stay, and Skitter divulges the confidential information she's happened upon, you could be just as culpable, face the same restrictions and penalties.''



Grue replied, ``So you want us to leave a teammate in your custody, here?  No.  That's ridiculous.  I can't speak for the others, but I'm staying.''



\emph{Teammate}.  He'd said I was his teammate.



There was a pause.



``All four of you, then,'' Miss Militia replied, sighing, ``I expected as much.  I simply thought you should be informed.''



``Skitter,'' she went on, ``Just to be clear, you would be well advised to keep your mouth shut, until we've come to a consensus here.  Or you could get your team in trouble.''



``Noted,'' I replied.



Armsmaster let me stand, but he settled his one hand on my shoulder, held on with an steel grip that left me no illusions about my ability to walk over and join my friends.  Ex-friends?  I wasn't sure where we stood.  I hadn't expected them to come to my defense.



Grue looked much as he ever did, a human shape wreathed in smoky darkness.  His skull mask showed through, when he was still like this, but his face was impossible to make out, let alone his facial expressions.  Even his body language was masked beneath the layer of darkness, when it was billowing around him like it was, making him seem larger.  I thought maybe he had his arms folded, but I couldn't be sure, and he had his feet planted shoulder width apart.



Regent looked a little worse for wear.  He was wet, dirty, spattered in blood, and he had a long cut running from the side of his neck to his shoulder, down to his elbow, all neatly stitched up.  I hadn't heard any alerts about him being taken out of action, so I assumed it wasn't that serious.  That, or it \emph{was} serious, and my broken armband hadn't caught the message.



Bitch, by contrast, looked to be in better shape than anyone present, physically.  She stared at the ground, hands jammed in the pockets of mud-caked, soaking wet jeans.  Her hair was wet, pulled straight back and away from her face.  A hard plastic dog mask was raised so it sat on top of her head, cord dangling.  She was intact.  Physically.



Mentally?  Emotionally?  Her dogs were the closest thing she had to family, and she had watched seven or eight of them die.  She was rigid with tension and repressed anger, but she didn't have anyone to direct it at, so it broiled inside her, just waiting for the slightest of excuses to be released and vented.  I wondered if Grue had told her to keep her hands in her pockets to keep her from lashing out and hitting someone.



Tattletale was on crutches with one leg bent to keep it away from the ground, had a bad bruise on her face, but was otherwise in one piece.  Her eyes darted to watch the three heroes and myself.



``Skitter escaped her restraints and uncovered another cape's secret identity, and we can't say for sure whether it was intentional or not,'' Miss Militia explained to the rest of the group.  ``In the interest of protecting that cape, who I assume isn't well enough to join the discussion\ldots?''



She looked at Armsmaster, who shook his head.



``\ldots{}We're left with three options,'' she finished her thought.  ``Jail time, especially if it's discovered that this \emph{was} intentional.  Joining the Wards under a probationary program-''



Regent snorted.



``Or, as a final option, some sort of collateral.''



``That option is generally reserved for capes we can trust,'' Armsmaster spoke, his voice low.



My pulse picked up as I heard Armsmaster's words.  This was a dangerous situation, all of a sudden.



``Collateral?  Explain?'' Grue asked Miss Militia, apparently not gathering the deeper meaning of Armsmaster's statement.



``This isn't the first time we've run into a situation like this, though this is a first for an Endbringer event that wasn't a blatantly intentional attempt to gather information on a rival.  In the previous case, the villain couldn't be detained conventionally, and the Birdcage wasn't yet running.  To top it off, he\ldots wasn't Protectorate material.  For reasons I won't explain.  Yet every individual involved was concerned that if we didn't resolve the case, it would be a costly loss of resources on both sides with an ongoing pursuit by the heroes, and there would be potential escalation leading to serious harm or death on one side or the other.''



Grue nodded, ``So?''



``So he agreed to reveal his real face to the other cape, so that any abuse of the knowledge on his part could or would be just as damaging to him.''



Reveal myself to Sophia?  No.  On so many levels, no.



``I'm sorry,'' I told her, ``That doesn't work either.''



Armsmaster tightened his grip on the armor of my shoulder until I could feel the pinch.  Miss Militia leveled a very cold look at me.  I saw Tattletale staring at me.  I met her eyes.  She was easiest to look at.



``You're making a difficult situation even more difficult for you, by being stubborn,'' Legend spoke.



``Knowing Skitter, I'm sure she has her reasons,'' Grue replied.



``She always does,'' Armsmaster replied.



Grue turned his head sharply to look at the hero.



\emph{No}.  He wouldn't.



``Well, you've made a good case,'' Tattletale spoke, ``Let me make mine?''



``One second,'' Legend spoke.  He turned to Armsmaster, ``I need more details on this group.''



``The one that is speaking is Tattletale, member of the Undersiders,'' Armsmaster spoke, his voice a hair away from being a growl, ``A master manipulator, penchant for head games, likes to pretend she's psychic but she isn't.  We don't know her power, possibly clairvoyance, psychometry, or some combination thereof, but we've got her pegged as a Thinker 7.''



``Seven?  I'm flattered,'' Tattletale replied, grinning.



``It's reason enough to end this conversation here and now,'' Armsmaster spoke, ``Before you find some angle.''



``Fine,'' Legend nodded, ``That's all I need.  Miss Militia?  Escort them away?''



Green-black energy leapt to Miss Militia's hand, materialized into the shape of a gun.  She didn't raise it, and she kept her finger off the trigger, but the threat was implicit.



``You start a fight here,'' Grue spoke, ``You better pray to some higher power that you can fucking spin this well enough with all those others looking, because it's an end to the truce if you don't, too many eyes on this.''



Grue turned his head, and I leaned forward a little to see what he was looking at.  There were capes at the far end of the hallway, staring at the scene, kept out of the main triage area by a set of PRT officers.  Trickster leaned against a wall with a cell phone raised, recording video.



``It's not a concern,'' Legend spoke.  ``Miss Militia?''



``Come on, let's walk,'' she told the others.



``No,'' Grue replied, his chin raising an inch, challenging, defiant.



Tattletale raised one hand, ``If  could just say my piece, I-''



``Quiet,'' Armsmaster interrupted her.



``Nobody ever lets me talk!'' she spoke, turning on her heel to walk away, flouncing, almost.  It was a bit theatrical, overacting.  I wondered if someone that didn't know her would catch it.  ``Whatever.  Grue, let's go.''



Grue looked at her.



``It's cool,'' she gave him a little smile, then she offered me one, ``Hey Skitter, don't sweat it.  We'll handle this, kay?''



``Kay,'' I muttered.  In a way, I was relieved at the idea of them leaving.  I had no idea what I'd do, but it was a relief anyways.



Miss Militia raised her gun a fraction, waved it toward the others to prod them onward.  One by one, they turned.  Tattletale led the herd in walking away, followed my Regent and Bitch.  Grue was the last to turn away, with Miss Militia following him.



When they were out of earshot, Legend floated over the counter to land in front of me.



``We've given you three options.  Pick one or I'll choose for you.''



I opened my mouth, closed it.  The only things I could think of to say would only get me in more trouble.



\emph{This working?  This on?  Good.  }The tinny female voice rang out from the armbands of the two heroes.



Armsmaster snapped his head around.\emph{  }I followed his line of sight to where Grue, Regent and Bitch were standing in between Tattletale and Miss Militia.



\emph{For those of you who don't have a front row seat, the very well armed Miss Militia is currently doing her best to point a Beretta 92fs at my head.  If this broadcast ends prematurely, you can all rest assured that the Protectorate is willing to kill and break the truce if it means censoring its dark, dirty little secrets}.



Legend grabbed me, hauling me into the air as he crossed the length of the room, Armsmaster hurrying behind as we raced towards the scene.



\emph{``Free speech is a wonderful thing, isn't it?''} I saw Tattletale's lips moving as she broadcast the message.  She wasn't holding any buttons down on her armband, but it was going through with no difficulty.  Miss Militia held a handgun pointed at Grue's heart.



Other capes were in the vicinity, some of the Travelers, New Wave, out of towners.  Not quite in earshot, maybe, but close enough to see everything unfold.



The heroine looked at Armsmaster as we arrived, ``She said something about deep access, offered your name, then the armband asked her for your password.  She knew your password.''



``Armband, pause announcement,'' Tattletale spoke.



\emph{Acknowledged}.  Her armband replied.



With his one arm, Armsmaster reached for his shoulder, but his Halberd wasn't there.  Photon Mom had apparently decided not to bring it when she'd carried him here.  No EMP burst possible.



``Let's negotiate,'' Tattletale spoke, taking a step to one side, ducking a little to ensure that someone else was always in between herself and Miss Militia.  Bitch scowled as the gun moved to point toward her head, with Tattletale roughly on the other side.



``Negotiate?'' Legend asked.



``Sure.  Let's turn things around.  You gave Skitter your three options.  Here's my three.  Number one: Shoot us now, and confirm to everyone in this room, civilian and cape alike, hero and villain, that you've got something to hide.  It doesn't even have to be lethal, people will still have their concerns if you knock us out rather than let us talk.''



Legend nodded, ``Okay.''



``Two: I do my little announcement, and the truce ends.  I really don't want to do that.  I recognize how necessary it is.  But if you decide that one cape's identity \emph{maybe} getting publicly revealed is worth the truce, well, that's on you, not me.''



``And the third option is that we release the girl,'' Legend guessed.



``You got it,'' Tattletale spoke.



``Except that you could be bluffing,'' Legend frowned.  ``You're a master manipulator, according to Armsmaster.''



``True enough.  You know, Alexandria was giving me a recap on what I missed, in exchange for my intel on the Endbringer.  Let's see\ldots Armband, find me the largest break in casualties from the earlier Leviathan encounter.''



\emph{Found}.



``Mark this time period.''



\emph{Marked}.



``The notifications in the minute before the mark?''



\emph{Sundancer down, ED-6.  Eschutcheon deceased, CD-6.  Herald deceased, CD-6.}



``What is the point of this?'' Legend asked.



``Please replay us the notifications following the mark, until I tell you to stop.''



\emph{Manpower deceased, CD-6.  Aegis deceased, CD-6.  Fenja down, CC-6.  Fenja deceased, CC-6.  Kid Win down, CC-6.  }Skitter deceased, CC-6. Kaiser deceased, CC-6.



``Stop.''



``What is the point of this?''  Legend folded his arms.



``Skitter's right here, she's not dead.''



``My armband broke,'' I replied.



``Did it?  Or did someone break it?''  Tattletale's gaze went to Armsmaster, her voice dropping in volume to ensure that our `audience' didn't hear.



``What are you implying?''  Armsmaster growled.



``I'm implying that you set things up to guarantee yourself a one-on-one fight with Leviathan.  Who cares, after all, if some villains get murdered in the process, if it means stopping an Endbringer?''



Armsmaster raised his voice, ``This is exactly the sort of manipulation-''



``Elaborate,'' the one spoken word from Legend was sufficient to cut Armsmaster off.



``Armsmaster has a fancy computer system in his suit, set it up to predict Leviathan's movements and actions.  Clockblocker tagged the Endbringer, put him on pause long enough for Armsmaster to set up the playing field the way he wanted it, with that predictive program.  Leviathan's going after the people who can make forcefields, and Armsmaster uses this, dangles Kaiser like bait, puts more villains – Fenja and Menja- in the way to Kaiser.  Sure enough, Leviathan marks Kaiser as a target, charges through the conveniently arranged villains, and goes straight to the spot where Skitter is.''



``Oh no,'' I heard Miss Militia mutter under her breath.



``This is nonsense,'' Armsmaster spoke, stabbing his index finger towards her, ``Heroes died too.''



Tattletale didn't hesitate a second in replying, ``To your credit, if any credit is due, that was an accident.  Your program can't account for that many variables, probably, in the chaos of a bunch of capes trying to keep Leviathan pinned down.  Either way, Leviathan did as you wanted, followed the path you plotted.  You used a directed EMP blast to nuke Skitter's armband, ensuring that she couldn't report Leviathan's position and call in reinforcements, buying you time to take on Leviathan one on one.  Who cares if she dies, after all?  She's a villain, and you're positive you'll win, that it'll be worth the body count you just allowed Leviathan to rack up.  Except you lost.''



Armsmaster scowled at her.



``This is a serious set of accusations,'' Legend spoke.



``Sure.''



``But it's speculation.''



Tattletale shrugged, ``Take Skitter's armband.  It'll have damage from the EMP hit.''



``You bitch,'' Armsmaster snarled, ``This is a lie.''



``Check the armband,'' Tattletale repeated, ``And you'll see the truth.''



``Convenient that this would take days or weeks to check,'' Armsmaster spoke.



``True, so how about I just do another announcement?  Tell everyone that's still wearing an armband an abbreviated version of the same story I just told you?  How do you think they'd react?  If you're really innocent, I'm sure your name would be cleared eventually, after the test results came back from the armband.  If it's wrong, we get get in \emph{everyone}`s bad books for fucking around with an Endbringer situation.  Hell, I'll even submit to being detained while you get things checked out.  You can take me from there to jail if I'm wrong.  Either way, you get some jerk in custody.''



Legend frowned.



Armsmaster lunged forward, swatting Grue aside with his armored hand.  He shoved Regent aside, reached for Tattletale.



A laser to the right shoulder spun him around, sent him sprawling to the ground.  His armor smoked where the laser had made contact.



``Who!?  Why!?''  Armsmaster flopped over, saw Legend with one open hand aimed at him.  ``Legend?''



Miss Militia pointed her handgun at his lower face.



``So, I'm guessing you don't want this getting out,'' Tattletale spoke, looking at the heroine, ``Let us walk away, I keep my lips sealed.''



``I know you were tired, that you hadn't slept all last night,'' Miss Militia told Armsmaster, ignoring Tattletale, ``Frustrated, your dream taken from you.  But to go this far?''



``It was for the greater good,'' Armsmaster replied, without a trace of shame or humility, ``If it had worked, Leviathan would be dead, the man holding Empire Eighty-Eight together dead.  All of us survivors would have been legends, and this city could have risen from the ashes, become something truly great.''



``It didn't work,'' Tattletale spoke, ``Couldn't.''



``Shut up.  You've said enough,'' Armsmaster spat the words, looked away from her, breathing hard.



``The way the Endbringer's physiology works?  You could detonate a small atom bomb in his face, he'd probably survive.  Take him two or three years to recover, but he'd survive.''



``Shut up!'' Armsmaster raised his head to shout at her.  He stopped, eyes flickering to me.  When he spoke again, his voice was almost calm.  ``You don't know everything.''



\emph{No.}



``Her,'' he pointed a hand at me, ``She's not who you think she is.''



I spoke quickly, ``Grue, shut him up.''



Grue raised his hand.  But he didn't blanket Armsmaster in his darkness.



``She's a wannabe hero.  Has been from the start, since the night Lung was first brought into custody.''



Grue's hand dropped to his side.



``I met her that night.  She said she was a hero, that you Undersiders mistook her for a villain.  I didn't think twice about it until she arranged a meeting with me, the night before the bank robbery.  Told me she had joined your group as an undercover agent, getting the dirt on you so she could hand that group over to us.  Talked to me again the night you raided the fundraiser, out there on the balcony.  Told me if I let her go, she'd get the details on your boss to me.  Guess she hasn't gotten around to figuring that little detail out, yet.''



I tried to speak, to say something, even `I changed my mind'.  My throat was too dry to form the words.



Armsmaster turned, shouted at the capes who stood watching, ``You want to look down on me!?  I tried to save this city, I got closer to killing the fucking Endbringer than \emph{Scion}!  That \emph{girl} is the person you should be mocking, spitting on!  A wannabe hero without the balls to do anything heroic!  Planning from the start to betray teammates for fame!''



I stepped back, swallowed hard.



``Is this true?''



I turned to look at Grue, but he wasn't asking me.  The question was for Tattletale.



``Yeah,'' Tattletale confirmed, sighing.



Bitch stared at me wide eyed, teeth bared, as if all basic human expression had left her as she regarded me.  Regent looked me up and down, turned away, as if in disgust, one fist clenched hard enough to make the area around the long stitched up cut on his arm stand out in white.



I couldn't see Grue's face, could barely make out his body language, but I knew that it would have stung ten times worse than anything else if I could see his expression in that moment.



Tattletale was the only one who didn't look surprised.



I backed away a step, and nobody moved to stop me.  The heroes were preoccupied with Armsmaster, the Undersiders couldn't or wouldn't go around the gathered heroes to follow me.



Some of the capes that were in the vicinity were staring at me.  Murmuring.  Panacea was among them, looking at me as though I were from another planet.



I turned and ran out of the hospital, out the door and into the street, kept running.



Except I had no place to run to.





