





How was a city like Brockton Bay supposed to pay its respects to all the heroes, villains and miscellaneous others that died to protect it?  Until about five years ago, the answer had been a funeral.



It really hadn't worked out.



On the surface, it was a great idea, had made for an amazing scene.  Grand speeches about great moments of true selflessness from even despicable villains, good guys doing the most heroic of sacrifices.



Except problems started to stack up.  Could the people in charge of the event really let someone stand up and give a eulogy for someone like Kaiser?  If they did, you earned the wrath of the dozens or hundreds of people who'd had their lives changed for the worse by Empire Eighty-Eight.



The uneasy solution had been to avoid saying anything about the local villains, beyond the fact that they had participated, but problems had stemmed from \emph{that}, too.  Subordinates or teammates of the fallen villains had made a scene over these omissions, sometimes during the funerals, and villain participation in Endbringer situations started to decline.



More issues came up, rooted in the reality that people who went out in costume were more theatrical or dramatic as a rule.  Too many vying to take the spotlight, hero and villain alike, even some of the fallen, with measures or requests placed in advance.  It didn't happen every time, but enough events became sideshows and media circuses that the whole purpose of the events was defeated.  The media was banned from recording the event, but the capes who'd sought to stand out only tried harder.  Fights had erupted.



So the funeral services became less frequent.  Then they stopped altogether.



A memorial was simpler.  All who had joined the fight could be treated equally.  There could be no snubs, really, nor could there be insults, dramatic oaths, taunts or speaking ill of dead rivals and nemeses before cameras or audiences of capes.  It was simply a dedication to the dead, a list of names, sometimes with a statue, if the groups involved could decide on something that didn't too closely resemble a particular hero or villain.  Ever a difficult, delicate balancing act.



Brockton Bay's memorial had no statue.  It seemed to be black marble with stainless steel in the core of the monument, so that the etched letters stood out in a metal gleam, even reflecting the sun's light if the time and viewer's position was right.  The overall shape formed an obelisk, with the corners and base unpolished and rough, only the four sides smoothed and polished.  It was out of the way, placed atop Captain's Hill, at the base of the mountains to the west of the city.  I wasn't sure if it was put there to stay or if they intended to move it after reconstruction and city revival efforts.



Even with the memorial being out of the way, set down in place five days after the attack, it had taken a full week before the worst of the crowds were gone.  Four times, I'd felt compelled to come see it and pay my respects, only to see the press of people and turn back.



Now I was here, along with a little less than a hundred people, only a small fraction of whom were actually viewing the obelisk.  Others sat on the hill or picnicked.  As strange and vaguely inappropriate as it seemed, I couldn't really blame them.  The memorial had been put here, specifically, because the rest of the city had been devastated.



In any given area of Brockton Bay, there was flooding, shattered streets, collapsed buildings, septic conditions or ongoing reconstruction.  Often three or four of those things at once.  More than half of the city was without power, two thirds had no running water, and even with the rest of the country and the world pitching in, uneven food distribution, health concerns, lack of facilities and rampant looting and crime made for dangerous living.  Buses were leaving every hour with evacuees, but the city was still thick with crowds of people just struggling to get by.  Too many were people who had no relatives or friends to go to, who wouldn't leave their remaining possessions behind to be taken by unscrupulous thieves.  Captain's Hill, for now, was a place that was safe, dry and clean.



I walked around the monument, noting the names.



Escutcheon / Tyrone Venson
Erudite / Mavis Shoff
Fenja / Jessica Biermann
Fierceling /
Frenetic /
Furrow /
Gallant / Dean Stansfield
Geomancer / Tim Mars
Good Neighbor / Roberto Peets
Hallow /
Herald / Gordon Eckhart
Humble /



Gallant was dead. Unsettling to think that I'd met him and fought him.   Or, rather, I'd fought against his team in the same skirmish, even if we hadn't actually paid attention to one another in the fight.  Now he was gone.



I could guess that the ones without names either hadn't given permission for their names to be released, hadn't written any will or had reason to keep their names private, protecting teammates.  I circled the monument, walking around to the right.



Impel / Corey Steffons
Iron Falcon / Brent Woodrow
Jotun /
Kaiser / Max Anders
Manpower / Neil Pelham
Mister Eminent /
Oaf / Wesley Scheaffer
Pelter / Stefanie Lamana
Penitent /
Quark / Caroline Ranson
Resolute / Georgia Woo
Saurian / Darlene Beckman



I noted Iron Falcon on the list.  A few nights ago, trying and failing to fall asleep, managing a half-sleep where my thoughts drifted, I'd made the connection between the boy I'd helped and the `Iron Falcon down' report I'd heard from the armband.  The name had maybe stuck with me because I could remember reading about how it was becoming a trend for heroes to go the easy route and stick -hawk or some other bird of prey on the end of their names.  Laserhawk, Flame Falcon, Steel Eagle, and so on.  It had become unfashionable, but apparently Iron Falcon had stuck with it.



If his name was here, it meant he hadn't made it.  Hadn't it been a problem with his leg?  How did that kill someone?  It was hard to figure out how I felt about it.  Disappointed?  Sad for him?



It was hard to figure out how I felt, period.  Not just about the dead.



I shivered, and rubbed my arms to warm up.  It was sunny out, but cool air rolled down from the nearby mountains, and the amount of moisture in the air made for a damp cold.



Should have brought something warmer to wear.  I stepped back and out of the way so a pair of parents with a toddler could pass by me.



Rubbing my sleeves against my arms, I traveled around to the right, to the far side of the memorial, which faced the city.



Sham /
Shielder / Eric Pelham
Smackdown / Jennie Ryan
Snowflake / Charlotte Tom
Strider / Craig McNish
Uglymug /
Velocity / Robin Swoyer
Vitiator /
WCM /
Zigzag / Bennie Debold and Geoff Schearn



It was shorter than the other lists, the last list of names, so there was space at the bottom.  Someone had used the empty space to etch words into the marble.  It was crude work, with scuff marks around each notch where the tool had been off target.  The letters were all in capital letters, all straight lines – the `o's were squares, the `B's two triangles joined at one corner.



KOOROW   BULLIT
MILK                   STUMPY
BROOTUS  JOODUS
AXIL         GINGIR



How long had it taken her?  She would have had to come late at night, well after the crowd had left, sat there with a chisel, hammer and flashlight, painstakingly chipped the letters into the marble.  If she even had a chisel.  She might have done it with a screwdriver or something else she had at hand.



I bent down and ran my fingers over the letters.



``Sickening.'' I glanced over my shoulder to see the father holding the toddler.  He shook his head, added, ``Vandalizing this?  So soon?''



``They're names, and this took time,'' I said in answer, turning back to the memorial.  ``They mean something to someone.''



``I think you're right,'' a girl said.



The father didn't respond, just continuing to walk around the memorial.  I waited until the father was gone before I stood, checked to see that most of the people who'd been visiting were off getting their lunches, the rest out of earshot.  I turned to face the girl, sticking my hands in my pockets.



Lisa'd had the sense to dress warmer than me.  Her hair was up in two tight buns, just behind her ears, and she wore sunglasses, an oversized sweater and a skirt with tights underneath.  She had a backpack slung over one shoulder.  She smiled lightly, almost sadly.



``You getting by?'' She asked me.



I shrugged, ``I've got a cot in one of the shelters for people who lost their homes, and I have some of the cash I brought with me, so I have the basics of what I need.  Not sure if Coil cancelled my bank account or what, but I might have that too.  I'm surviving.''



``I figured you would be.  What I want to know is if you're \emph{okay}.''



I shrugged.  How did I respond to that?  Confess that I wasn't sleeping?  That I had nowhere to go?  That I was angry enough in general that I'd been asked to leave one shelter, for yelling at someone who hadn't entirely deserved it?



Could I even bring any of that up?



Instead, I guessed, ``So.  You knew?''



``Yeah,'' Lisa replied, bobbing her head in a nod.  ``I'm so sorry.''



``You're apologizing?'' I asked, caught by surprise, ``I'm the one who planned on screwing you guys over.''



``But you didn't.  You changed your mind.  Me?  I had an idea of what you were up to, I lied to you, misled you.  Manipulated you.  Kept it all a big secret.  And I'm sorry for that.  Really.''



``How long did you know?  When I was lying on my cot in the shelter, wondering whether you did know, thinking back to your expression and the things you've said in the past, I thought maybe it was when I decided to leave the group over\ldots''  I paused, looked at the people nearby, who might or might not be in earshot.  ``\ldotsyou know.  But no.  You've known from the start.''



``Since before we met.''



That was unexpected.  ``What?  How?''



She turned her head, surveying the scene, the handful of people still around the monument, ``Over there?''



I nodded.



We walked over toward the railing above the sheer drop to the base of the hill.  The position gave us a view of the entire city.  There was the ocean, the coastline with crews and machinery clearing away the wreckage of buildings and the PHQ.  Blinking lights marked the barriers and trucks around the perimeter of the massive hole Leviathan had made in the upper end of Downtown.  The hole was still largely filled with water.  People were still trying to verify if it would ever empty on its own, or if it would be a permanent part of downtown.



I couldn't make out the details of the Docks, but I saw flattened and ruined buildings.  I'd scouted it early one morning, pulling on my costume and traveling the streets at an hour that even the roving mobs were asleep.   From a distance, with the help of my bugs, I'd verified it.  The loft was gone.



My dad's house was intact, at least, if not in the best shape.  Still, even with two nights in a row with barely three hours of sleep between them, I'd held off on returning.  Too much I couldn't explain.



Lisa leaned on the railing, ``I didn't think we'd win.''



I joined her, leaning beside her.  Maybe she could read something in the fact that I put myself far enough away that she couldn't reach out and touch me, couldn't push me over if she had a mind to.  Paranoid.  Looking over the city, thinking of the devastation, the hundreds of thousands of hungry, dirty, homeless people still in the city, I thought aloud, ``Did we?''



``We're alive.  That's a win in my book.''



I didn't respond, and a silence stretched between us.



``Okay,'' Lisa told me, ``No more secrets.''



``Sounds good,'' I admitted.



``And I'm trusting you to use that brain of yours to know what parts of what I'm about to say should stay between us.''



``Okay.''



``Imagine this.  You walk down a street in an unfamiliar city, you've got an appointment to go to, but barely any directions.  You follow?''



I nodded.



``You come to a branching path.  Do you go left, do you go right?  Whatever decision you make, you've got to live with it, walk down that path, and if it's wrong, you have to figure out how to get over to the other path.  And that keeps happening, until you get where you need to be.  Maybe you got lucky, picked the right paths, got there on time.  Maybe you were unlucky, and you were late.''



I nodded, not sure where this was going.



``That's everyone's situation, day-to-day, making choices.  Through resourcefulness, like using a cell phone to call for directions in our hypothetical situation, or talent, like me using my power, we can make it more likely we find the right paths, but we inevitably come to a choice between A or B at some time, right?''



``Right.''



``What if you could choose both?  Choose both A and B, so your A self knows what your B self knows and vice versa.  When you know path B is the right choice, you can make it so.  The world where you chose to go down path A is gone, vanished, so when you comes to the next choice, you can do it again.''



``Sounds pretty useful.''



``Trick being that you can only have two realities running in parallel at a time, and the only differences between those realities hinge on the choices and calls you make.  So you delegate.  You find people who will follow orders.  Sometimes you send them out to do something in only one world, so that if things don't go the way you want, you can default to the reality where you didn't send them.  Or, in simpler terms, in one world, you flip a coin.  In the other, you hold on a second, delay, say something.''



``Until every coin you're flipping gives you a heads.  You're talking about Coil,'' I realized.



Tattletale nodded.



``He's been doing that from the start?''



``Some.  The bank robbery, he had our back.  But timing was sensitive, and I guess he wanted to maximize the chances that he'd get Dinah, so he didn't have a concurrent reality where he kept us out of action.  And, according to him, we succeeded in both cases, though Bitch got hurt in a fight with Glory Girl in the other one.  Lucky for us, I suppose, that the world where she \emph{didn't }get hurt was the same one where Coil got his captive.''



I winced.  Even an offhand mention of the role I'd played in what happened to Dinah elicited a painful stab of guilt.



``We didn't have him for the fight with Bakuda, but we did have him for the fundraiser.  He had the other version of us in reserve.''



``And the fight with Empire Eighty-Eight?''



Lisa frowned, ``Apparently that was one case where he saved our hides.  Remember that call I got?  Telling me to be careful?  Same thing he did with the bank robbery.  Tells one version of me to push us to be careful, tells the other to go in for direct confrontation.  Knowing how he works, I try to nudge us in one direction or the other.  The group of us that went in for the headlong attack?  We got taken down.''



``That happened?'' my eyes widened.  That would have been the fight with Night and Fog, and it hadn't been pretty as it was.  ``Did we die?''



Lisa shrugged, ``Not sure.  He didn't elaborate, often doesn't, unless it's key info.  But Coil decided \emph{not} to go with that option, so it was clearly worse than what did happen.  Or worse in his eyes.''



``Damn,'' I muttered.  What had happened?  Not knowing was almost worse than hearing we'd all been slaughtered.



``Anyways, point of this explanation is this:  Knowing we had an imminent fight with Lung coming, knowing Lung planned to pyrokinesis our general area until he rooted us out, got civilians to finger us or brought in enough capes to make life difficult for us, I called Coil.  He said he'd help, told us to wait five minutes, then take the more direct route, straight into the heart of ABB territory.



``We go, we take out a contingent of ABB gangbangers and scare off Oni Lee.  Then I get a call back from Coil.  The other reality?  We left earlier, went a different route.  Got in a fight with Lung before you showed.  You decided to attack \emph{both} our groups while we were occupied fighting each other, worn out, only Lung was stronger at that time, too strong for you to do too much.  By the time you realized you'd have to work with us to stop him, which wasn't long, it was too late.  Lung was too tough.''



I tried to picture that scenario.



``I got away, managed to call Coil, let him know what had happened.  Coil, in turn, informed me in \emph{this} reality, the one you remember.  Told me to watch out for a junior hero in the area.''



I nodded.



``So I told the group to hold up, fibbed a bit about needing to use my power, get a sense of things, like Lung's location.  I was hoping that you were a new member of the Wards, that you'd call in help and deal with Lung without our involvement, that you'd leave, or even start the fight on your own.  You attacked him on your own.''



She shrugged, smiled a little, gave me an apologetic look with a tilt of her head, ``And my plan worked out.  Of course.''



``Of course,'' I replied, dryly.



``It might have ended there, but then Grue mistook you for a villain, and you didn't correct him.  It was interesting enough that I played along.  The idea of recruiting you came when he was finishing his introductions.''



``So everything I've been through, all of this, it's-''



``My fault, pretty much.  That's why I'm saying I'm sorry.  I mean it, too.''



I sighed.



``It's okay,'' I told her.  ``I think\ldots I think if it happened again, I'd still want to be part of the group, want to have met you guys.  I'd want some stuff to go down differently.  Dinah, my dad, having things come out like they did after the battle with Leviathan.''



``We can't take back what happened,'' Tattletale said.  ``But we can try to fix it.  Some of it.  You could go back home.  Face the music.  Tell your dad some or all of what happened.  You could go somewhere else, or I could convince the others to leave you and your dad alone, if you wanted to do that.''



``I'm not ready to go home just yet.''



``No?  I mean, I knew you hadn't gone home yet, but I thought maybe that was our fault, you protecting your dad, staying away from places we'd know you frequent.''



``I'm still hurt, still mad at him.  Mad at myself, too.  I guess, more than anyone, I expected my dad to understand, to give me the benefit of a doubt.  And going home would be going back to the way things were, which is the last thing I want.''



``So you don't want to go home, you obviously don't want to go to the Birdcage, and you turned down an offer to join the Wards.''



I hesitated, ``Yeah.''



``So, what are you going to do?''



``I don't know.''



``Become a hero?  Strike out on your own?''



I shook my head, stressed the words, ``\emph{I don't know}.''



``No hard feelings if you want to go that way.  Again, I can talk to the others, ensure they don't go straight for revenge or any of that.  We don't hate you, now, hurt as some of the others might be.  Except maybe Bitch.  She probably hates you.''



``\emph{Really}, I don't know,'' I told her, exasperated, ``I don't \emph{like} or even respect any of the heroes I've met, I don't even see the point of it.  As villains, we faced down other villains.  It wasn't so different from what I'd be doing as a hero\ldots but what did we really accomplish?  What does anyone accomplish, if all we end up with is \emph{this?}'' I gestured out at the cityscape stretching out below us.



``Maybe you don't know what you want to do because what you \emph{really} want to do is come back.''



I didn't reply for a minute.  The quiet was disturbed by the noise of not-too-distant helicopters moving over the city, some capes flying alongside them as guards.  It would be another drop of much-needed supplies.



I sighed, ``They wouldn't have me, and those guys won't budge on the thing with Coil and Dinah.  Not really.''



``Probably not.  I mean, even \emph{if} they took you back, you'd have to eat crow, accept a few concessions, like Coil's `pet'.  There'd be no more playing around.  You'd have to go all-in, from here on out, if you expected to convince them you were legit.''



I shook my head.



``You want to be forgiven for what you did?  It's not going to be easy.  There's going to be a sacrifice on some level.  And that starts with giving up that stubbornness, being willing to talk to them.  To talk to \emph{me}.  You might even change your mind, find yourself able to look past thing with the girl, for the sake of having friends, doing the things you want or need to do in other areas.''



I stood away from the railing, stuck my hands in my pockets to keep them warm.  ``Never.''



``Never's pretty final.  If you're so certain, what do you have to lose by hearing everyone out?  Hearing \emph{me} out?  I've got coffee and lunch in my bag, we can sit down, talk it all out.  If you're willing, we can then go meet the others.  I'll talk to them with you, back you up, keep Bitch from murdering you.''



I shook my head, turned and rested my back against the railing, looking at the memorial, rather than the city.



So many dead.  So pointless.  What was wrong with this world, that it was this fucked up?  That people like Sophia and Armsmaster were heroes?  That there couldn't even be a proper funeral for the people who had given their lives, because of a small handful of grandstanding idiots?



The wind blew hard from the north, cold, blowing my hair into disarray.  I pushed my hair out of my face, tucked it behind my ear.  When I gave Lisa a sidelong glance, she was putting her hood up.



She spoke without looking at me, ``I'd go on, ask about whether you prioritize friends or morals, talk about how you've grown as a person in so many ways since joining us, except my power informs me that you just settled on a decision.''



She was right.  As I stared at the monument, a goal was crystallizing in my mind, a focus.  I knew, now, what I wanted to do.



I had to change things.  I had to be better than them.  Than Armsmaster, Sophia, Coil, and all the others.



``Yeah,'' I replied.  She turned to glance my way.



``And does this plan feature the Undersiders?''



I gave her my answer.





