





``I think we've got a stray, Tasha.''



Tasha frowned as she looked up from her cell phone, and looked to where Daniella, behind the register, was pointing.  Her lip curled in distaste.



It was a girl, fourteen or fifteen, with dirty blond hair – both in the sense of being greasy and in color – tipped with streaks of blue.  Her clothes looked like they had only barely made the cut for the goodwill bin, and had been worn for weeks or months since she'd gotten them.  The girl was pretending to look through a collection of jackets that were still left over from last spring.  People like that weren't supposed to be able to walk around the Boardwalk and bother people.



``I'll handle it,'' Tasha told Daniella.



She quietly cleared her throat, straightened her back and approached the girl with a fake smile plastered across her face.  ``Can I help you?''



``I'm good,'' the girl shoved one jacket to the other end of the rack, and Tasha couldn't help but imagine a fingerprint being left on the leather.  She wouldn't be able to get that image out of her head until she evicted the kid and chedcked over the jacket herself.



It bugged Tasha that the girl hadn't left.  Most cleared out when confronted, well aware they were in the wrong place.



``I'm going to be blunt, then.  You can't afford these jackets.  That one you just pushed aside?  That's a design by Fendi.  It's over four thousand dollars.''



``No shit?  It's ugly.''



Tasha pursed her lips, glanced at the other customers in the store.  A pair of college-age girls, a woman and her boyfriend.  Nobody seemed to have heard the vulgarity, or the crass insult.



Leaning close, Tasha hissed, ``Do I need to call security, you little idiot?''



`Security' served as a euphemism for the enforcers on the Boardwalk, paid uniforms who patrolled the streets and the stores, keeping an eye out for the homeless, gang members and shoplifters.  Their methods were as blunt as methods got.  Victims generally weren't in a position to go to the cops and complain, or the police simply overlooked the enforcer's activities.



``I \emph{really} hate being called stupid,'' the girl spoke, meeting Tasha's eyes with a glare.



``You must be new around here if you aren't-``



``Shut the fuck up,'' the girl interrupted her, with enough force and hostility that Tasha stopped mid-sentence.  ``Breathe in my face again and I'm gonna gag.  Your breath smells like vomit and a halfhearted attempt at covering up the smell with candy.''



Unconsciously, Tasha's hand rose toward her mouth.  She stopped and folded her arms, as if to prevent her hand from straying again.  She tried to gather her composure, tell off the girl, but the girl was already speaking.



``Your boyfriend is cheating on you, Tasha Fowler, sleeping with your best friend.  Pretty fucking ironic, given how unattractive your friend is, and your continued attempts to puke yourself thin and make yourself pretty for him.''



Tasha felt a cold feeling in the pit of her stomach.



``If you hurry and run the entire way, you can catch them in the act.  But you can't waste a second.''



``How do you\ldots?''  Tasha asked, but the girl was already looking through jackets again, clearly not listening.  Tasha glanced at the door.



``Go!'' the girl suddenly barked at her.  Startled, Tasha moved toward the door, and then she kept moving, running.



As the saleswoman left the store, the door banging closed behind her, Daniella stared first at the door her coworker had just escaped through, then at the ratty little girl.



The girl turned her head, pretending to examine a jacket, so she could hide a vulpine smile that spread across her face.



\blacksquare



They arrived on site in a clap of thunder.  She almost lost her footing, but Grue offered her a steadying hand.



The downpour immediately drenched every part of her that had still been dry when the tidal wave crashed into the lobby.  She used her hands to pull her soaking hair back out of her face, combing it back into place with her fingertips.



``He's down there, Tattletale,'' Grue spoke.



``Yep,'' she replied.  Leviathan was in the midst of the shattered Boardwalk, pushing one section of the wooden walkway out of his way with the tip of his tail.



``Bigger in person,'' Regent spoke.  His normally loose fitting shirt clung to him.  After moving his arms and watching the water dripping off of the soaked sleeves, he pulled it off, so he wore only the closer-fitting mesh armor he'd had on beneath.



Tattletale grinned.  Sometimes you couldn't do anything else.  ``We are so fucking out of our depth.''



``Everyone is.  Even Legend,'' Grue replied.



``Listen,'' she said, ``If I die-``



``None of us are dying,'' Grue spoke, his voice hard.



``Odds are one of us is going to.  Statistically speaking,'' Tattletale pointed out.  ``As there's only four of us\ldots''



``Three.  Bitch isn't here and Skitter's not in the group,'' Grue spoke.



``Right,'' Tattletale answered.  She looked for Skitter and spotted her in the jumble of people, on her hands and knees in the receding waters from the tidal wave.  The girl stood, coughed a few times, water spraying from the fabric of her mask, then turned her attention to surveying the scene in that peculiar way she did.



Skitter was so focused on the scene that she didn't even seem to notice the bugs congregating around her.  More than one out-of-town cape gave her a weird look when a bug flew by, to settle on a wall or somebody's shoulder, but the girl was oblivious.  Maybe she was so used to being self conscious and imagining people avoiding her or looking at her funny, she couldn't see it when it was real.  Funny, that Skitter had turned her ability into such an effective tool for sensing and assessing her environment, yet she was so unaware of some things.



\emph{She'd be better at using my power than I am.}



Skitter had a piece of wet paper hanging off her shoulder, some trash that the wave had picked up, but there was nobody to point it out or pick it off.  She was alone.  Tattletale felt a pang of sympathy.  She'd never been able to stand being isolated, had always had her family, with roommates, friends and fellow squatters living with her after she'd run away.  Taylor, though, seemed to gravitate towards solitude.  She pushed people away, and when it came down to the nitty-gritty, when their group had found out the details with the kidnapped girl, Taylor had left.  Tattletale couldn't imagine doing the same thing, and she had strong suspicions Taylor was closer to the others than she was.  It was a damn shame that things had gone that way, because she been blossoming as a person, lately, actually connecting to others.  To \emph{Bitch}, even, of all people.



Tattletale couldn't help but feel regret, too.  She had to admit the schism was at least partially her own fault.  Not paying attention, not getting the right info.  Tattletale couldn't help but feel she should have been watching out for this sort of thing, knowing that it would take so little to spook the most sensitive member of their group.



She'd grown lax.  It had been easy to, with the knowledge and comfort of the fact that Coil's power gave them something of a safety net.   But when she'd phoned, informed him, her fingers crossed, he'd told her that he was already focusing on other things.  He could only make the call on one series of events with his power, after all, and in the wake of the Endbringer's arrival, he had greater priorities.  The opportunity had been lost.



``\emph{If I die},'' she spoke, leaving no room for further argument, ``An envelope should arrive in the mail for me, a week or two after I've bitten it.  I wrote it.  It's got all my passwords and account numbers for the money I've set aside, so far.  You guys take it, give some to Taylor if you run into her.''



``Alright,'' Grue spoke.  Tattletale quirked an eyebrow at him.  She'd expected more resistance.



``And if you happen to get yourself killed, we'll make sure Aisha gets what she needs.  Just so you know.''



He didn't voice a response, but he nodded once.



She cast another glance Skitter's way.  She should've asked, before they parted ways.  Would Taylor want her dad to know what she'd been up to?  It was impossible to say.  Taylor wouldn't want her dad to know about her villainous activity, but to at least have him know she'd gone out as part of a huge sacrifice like this?  Maybe.



``Get Ready!'' Legend cried out.



Tattletale grinned, turning her full attention to the Endbringer from beneath the waves.  It was crouching, preparing to charge.



Using her power wasn't a switch she turned on.  It was letting the walls come down, letting the information start pouring in.  It meant a killer migraine if she used it too much, especially on people or living things, but if she had a headache three hours from now, it would be a damn good thing.  It would mean she was alive.



\blacksquare



Getting rid of the saleswoman had been easy-peasy.  The bit about the cheating boyfriend had been an outright lie.  In a similar vein, the part where she'd mentioned the best friend had been an educated guess, but the salesgirl, Tasha, wasn't the type to have a friend prettier than her.   The way she'd obsessed over her phone and the revelation about the eating disorder were clue enough that the woman had been deeply insecure.  By the time she realized she'd been played, she would still feel compelled to hurry home and check.  Probably bad karma to leverage that sort of weakness, but it meant getting one obstacle out of the way.



The woman had been a bitch anyways.



Lisa watched out of the corner of her eye as the cashier picked up the phone, her eye on attitude, posture, body language, volume of speech.



\emph{Worry; calling coworker, not getting response.}\emph{Quiet, hushed; hiding anxiety from customers.  Wants to convey professionalism, confidence.}\emph{Anxiety, wants to convey professionalism: new to the job, only started two weeks ago.  Doesn't know how to open safe: not much money in register.  Doesn't know how to close store alone.  Still no response desperately needs break for bathroom and to sneak a smoke not allowed to smoke on the job looks bad for customers and manager has hard stance on it making clothes smell.}



Lisa closed her eyes briefly, took a small breath to center herself.  This power was new, untrained.  It had a way of running away from her, overwhelming her and leaving her bedridden with headaches if she wasn't careful.  People were too random, too chaotic, too complex.  She could only push herself like this for an hour or two every few weeks before she started to suffer.  It was getting better over time, as far as her tolerances, but the rate of improvement was agonizingly slow.



No, she had to focus on the essential detail: the girl behind the counter wasn't calling security.  This was good.  And given the other bits of information Lisa had picked up, she could be sure the cashier would probably be calling other coworkers before getting someone to kick her out of the store.



Which meant Lisa could do what she came here to do.  She turned her attention to the man that sat on the leather covered bench by the change rooms.  Thirty-something, wearing fashionable clothes and a nice jacket that was perhaps a bit too big for him, hair recently cut.  He waited with his attention on his smartphone, while his girlfriend or wife tried on something.  Deserving of a little more scrutiny.



\emph{Expensive clothes, expensive phone; wealthy.}\emph{Confident, patient despite being in a position many guys hated; mature, adult.  Clothes style match his personal tastes, not the type to dress according to girlfriend's tastes. Tall, athletic: exercise habits developed in military but not currently enlisted this ties into confidence and patience he's used to waiting and-}



She stopped.  Needed to get back on track.  Just needed a starting point to get at the stuff he'd keep secret.  Confidence, military.  How would he pick a four digit number?



\emph{Confident and military trained; goes out of his way to keep numbers random.  Looks early thirties; born late 70's.  Tendency to go with higher number to start.  8 or 9, mid-range number like four, five or six, then high, low, no repeating numbers.  Dressing in darker jacket, pants, trimmed beard, conservative; number will be even-even-odd-odd or odd-odd-even-even.}



``Something else,'' she murmured to herself, as the flow of information began to slow.  If it slowed enough, it meant that there weren't enough points of reference to generate new data, it could even mean her power would start supplying information based on speculation or falsehoods.  She chanced a look at the cashier, but the girl was studiously ignoring her, for the time being.



She looked back to the man.  Shoes were nothing special.  No logos or brand names on anything he wore, that she could see\ldots but he was using his left hand on the touchscreen of his phone.



\emph{Southpaw; tendency to go for numbers on left side of keypad, eight, then four, seven, then one or three.  One.  8471.}



Good.  And his wallet\ldots



\emph{Southpaw, confident; wallet in left jacket pocket.}



He was distracted.  She abandoned the coat rack and approached the man, being careful to stay directly behind him, in his blind spot.  His jacket was unbuttoned, and the end with the pocket was draped beside him on the bench, the pocket facing her.  Easy grab.



\emph{Wallet in left jacket pocket; intended to help mask presence of gun holstered at left hip.}



She turned a hundred and eighty degrees on the spot and walked back the direction she'd come.  Concealed gun?  Not worth it.



Her retreat stopped when she saw the man that was entering the store.  Maroon uniform, cap, belt.  One of the enforcers from the Boardwalk.  \emph{Shit}.



She glanced at the cashier.  She didn't need her power to read the girl's look of surprise and relief to know that the girl hadn't made the call.  Bad luck?  She looked at the enforcer.



\emph{Moving with purpose, going out of his way to avoid looking at her; most definitely coming for her.}



Had it been the girl she'd scared off, Tasha?  Probably not.  Did it matter?  She turned and looked for another exit.  The boyfriend with the smartphone was standing up, saying something to his girlfriend in the changing room, walking towards the clothes rack.



\emph{Placing himself in way of exit, position of hand; preparing to draw on her if she gets too close to making a run for it.  In cahoots with the enforcer.}



\emph{Which }could only mean one thing.  She looked back at the enforcer that was getting closer to her.



\emph{Working with the `boyfriend'; Not an enforcer.  Ex-military.  Has gun.}



To top it off, the girlfriend was leaving the changeroom, talking cheerfully to her boyfriend as he pulled a dress off a rack.  Her hand was too close to her oversize bag, which was open.  That one was a gimmie.  A team of three, each with guns, all of whom were after her.



\emph{Trap.}



``No kidding,'' she muttered to herself.  How had they tracked her down?  She had been careful to stay out of sight of security cameras, and she had avoided poaching at the same location more than once.  She'd used a different ATM each time she drained some rich schmoe's bank account, hidden her face from the hidden cameras at each.



She bolted, shoving a display of sunglasses on top of the enforcer, ducking around to his right, out of his reach.



It was a miscalculation, he didn't care about the sunglasses.  He pushed the rack to the ground, hard, and closed the distance with a single long step.  He had superior reach, strength.  His fist swung in one fluid movement with his step forward, striking her in the stomach, just below her ribcage and off to one side.



\emph{Striking solar plexus; trained in martial arts, striking to inflict maximum pain, disabling-}



``Urggunnnh,'' she swore, as she crumpled to the ground.



``Oh my god, oh my god, what the fuck did she do?!  The merchandise!'' The cashier shrieked, shrill.  ``I'm going to be in so much trouble, oh my god.''



``Phone the security office after I'm gone,'' the not-enforcer spoke, ``My supervisor will take it out of my pay.''



``Oh my god,'' the cashier spoke, hands over her mouth, oblivious to his words.



``He-'' Lisa began to speak, then grunted and choked as she was heaved up to her feet by the back of her shirt.  The not-enforcer twisted the fabric of her shirt until his hand was knotted up in it, the collar tight against her throat.  ``He's not\ldots''



She gave up before going any further with her protests.  It didn't matter.  Nobody would believe her.  A ratty young teenager from the poor part of town, being paranoid about the cops?  Nobody would step in for her, here.



``I'll talk to her,'' he spoke.  ``Let's see.''  He patted her down with his free hand, brusque, not giving a second's thought to the fact that she was a girl and a minor.  He reached his hand into her back pocket and when he pulled it out, he had a small knife clasped in it.  Not hers.  He placed it on the counter.



The cashier stared at the knife, eyes widening, then she turned her attention to the merchandise.  Ignoring him.  What the enforcers did wasn't something that few bystanders were willing to dwell on.  But these people wouldn't step in.  Not for a potentially dangerous teenager that had been carrying a concealed weapon.



Had he been a real enforcer, Lisa would be scared enough.  There were stories.  People having their fingers broken for shoplifting, being beaten insensate, and there were even tales of the rare girl or boy getting raped by the \emph{really} twisted fucks.  When the enforcer was done making \emph{sure} the offender in question wouldn't come back to the Boardwalk, they left the bloodied person in the back of an alley, worked with another to stick them in a dumpster, or if it was late enough that nobody would see, they would toss them off the side of the boardwalk.  A fifteen to twenty foot drop, depending on the tides and the location of the drop, onto sand or into water that was freezing cold for half the year.



He marched her out of the store, heaving her to the right to keep her from bumping into the doorframe.



He wasn't an enforcer though.  And he had a gun.  The looming punishment was a little more final than what the enforcers tended to pull.



\emph{Has gun; has killed before.}



He might kill \emph{her}.  It wasn't like she hadn't done something worth killing over.  She'd drained people's bank accounts, pocketed the funds.  Thousands of dollars, sometimes.



A spot of light hung in the center of her vision.  She'd pushed too hard with her power.  She'd have to conserve the use of her power, now, or the migraine would knock her out cold when it arrived in force.



There were people all over the Boardwalk.  The tourists watched with idle curiosity while the locals averted their eyes.  Such a contrast there – the locals \emph{knew} what was up.  It was just inconvenient to pay attention to it.



He forced her into a side street, then rounded a corner so they were behind the row of stores.  He shoved her against a wall, held her there.



She spoke, ``Tell me what they're paying you, I'll double it.  I won't have the money right away, but-``



``Not negotiating,'' the enforcer spoke.



A few long seconds passed.  She pushed the welling nervousness down, did her best to offer him a smile with her face smushed against the brick.  She asked him, ``What's next?''



``For now, we wait.''



Waiting she could live with.  Waiting wasn't getting shot and left for some store employee to find as they took out the trash.



It took a minute before the boyfriend and girlfriend rounded the corner.



``Marcus, you know that's no way to handle a lady,'' the `girlfriend' spoke.  She had a posh English accent.  When she spoke again, the accent remained, but the upper class lilt was gone, her voice serious, ``Turn her around.''



Marcus, the `enforcer', hauled on Lisa's shoulder, flipping her around, before planting his palm on her collarbone and pushing her back against the wall.



The `boyfriend' was holding a phone to his ear.  He handed it to the English woman.



``You have a phone call.  We advise you take it,'' the woman smiled at Lisa.



Lisa accepted the phone and held it to one ear.



```Sup?'' she injected playfulness and good humor she definitely didn't feel into her voice, grinned for the benefit of the three adults with guns.



``I apologize for the manner of our meeting, I hope my soldiers were not too rough on you, Lisa Wilbourn,'' the voice on the other end was smooth, calm, unruffled, ``Or is it Sarah Livsey?''



``Either or,'' she replied,  ``Lisa these days.''



``As you wish.  I have been watching you for some time, Lisa Wilbourn, I have become aware that you are something special, and I would like to buy your services.''



\emph{Word choice, buy vs. hire: large amounts of money involved.}\emph{ Word choice, buy vs. make an offer: not really a negotiation.}



She glanced at the weapons the three hired guns had in hand.



``I'm listening.''



\blacksquare



Leviathan whipped his tail around, slamming it through the ranks of capes.  Immediately after, a lash of water followed in the wake of his movement, cutting down yet another line of gathered heroes and villains.  The armbands announced the losses to the defending side with every attack Leviathan made.  Tattletale hung back, further than even the ranged attackers, and watched.



\emph{Steady blood flow from small wounds, asynchronous movement; has blood but no comprehensive cardiac system}\emph{ No cardiac system, no mouth, no nose, no apparent ears: nonstandard nervous system.}



``Educated guess says your power doesn't work so hot on him,'' she told Regent, as the two of them backed away.



``Fuck, no.  If I \emph{can} do something, my power's probably gonna backfire like crazy, and I think that bastard's quick enough that he's not about to fall flat on his face.''



Tattletale glanced at where Skitter was hurrying to assist one of the wounded.  Even knowing Taylor was out of earshot, she was careful to lower her voice, ``And I guess your secret weapon isn't going to work either?''



``Take two or three times as long, probably, if it worked at all,'' Regent grumbled.  ``Fuck, I'm useless.''



``Then use that first aid training Grue made us get, help out, and keep an eye out in case your power's needed.''



Alexandria flew toward Leviathan like a black arrow.



Leviathan charged forward as if to meet the heroine in a head on collision, then stopped abruptly.  His `echo', like a model of himself shaped out of water, continued forward with the same momentum he'd had while sprinting forward.  The heroine used her hands to break the surface tension of the water with a deafening crash, plunged through the water and out the other end, toward Leviathan.  She caught him around the neck and slammed him down against the road hard enough that even Tattletale, at the rear lines of the battlefield, had to adjust her footing as the impact rocked the ground.



Whatever advantage Alexandria had gained, it didn't last long.  Leviathan's tail snaked up and around the heroine's neck, catching her.  He whipped her into the ground, beside him, up into a wall, then back down.  This time, he held her beneath the water, using one claw to help pin her.



Dragon, racing forward through the air with an earsplitting roar, launched the full complement of missiles she had on her suit.  Before the munitions even struck Leviathan, Dragon was shedding the jet engine atop her, the missile launchers, and other extraneous devices, much as a space shuttle cast off pieces of itself as it launched.  The suit collided with Leviathan a half second after the missiles exploded against his torso and shoulders, and steel claws gripped his limbs.



The `face' of her armored suit opened up and began discharging a blue-white flame into his face.  The `flames' didn't move like flames should, spilling off him and down into the water, where they pooled on the road and continued to burn – after a fashion – beneath the water.  Leviathan, for his part, began tearing into Dragon, clawing away layers of armor with each swipe of his claws, almost uncaring as to the liquid fire that was spilling over him..



Between the smoke from the missiles and the steam that arose where the liquid fire touched water, Tattletale was having trouble seeing the battle.



Tattletale pressed the two buttons on her armband, ``Give me a flier to get me to a better vantage point.  Moderate priority.''



It took only ten seconds before one of the Silicon Valley capes arrived.  The man with the jetpack gripped her wrists and carried her up a dizzying height to the roof of the nearest building, five stories tall.  She moved to the edge, being careful to stay out of the way of the other capes that were already set up, raining bullets, flames, lasers and other projectiles down on Leviathan at every opportunity.  The Endbringer was still battling Dragon, had dug deep enough through metal and armor to reach the center of her suit.



Dragon ejected, skidded to a stop eighty feet away, a smaller suit of armor with thin arms and legs, each tapering down to points.  The suit Dragon had left behind glowed red, orange, white, then exploded violently around Leviathan, as though every crevice had been packed with high explosives.  Leviathan reeled, lashed his tail, and then lunged back toward the gathered capes.  He was intercepted by three flying capes this time, who harried him with superstrength and the case of one hero, an oversized battle axe.



\emph{Dragon enters battle with suit packed with explosives, risky, current suit has insufficient room for arms and legs: Suit unmanned.}



Remotely controlled?  Tattletale raised an eyebrow.  She hunkered down to to watch the fight, mentally opening those doors that let more information flow.



\emph{Leviathan, nonstandard cardiac, nervous systems: irregular biology.  No standard organs or weak points.  No brain, heart or center of operations for rest of his body.}\emph{ Irregular biology, no vulnerable organs: body divided into layers, extending down to hyperdurable core body, each layer down is slightly more than twice as durable as previous. Exterior skin is hard as aluminum alloy, but flexible, lets him move.  3% deeper in toward core of arms, legs, claws, tail, or .5% in toward core of head, trunk, neck, tissues are hard as steel.  6% in toward core of extremities or 1% toward core of main body/head, tissues strong as tungsten.  9% toward core of extremities, 1.5% toward core of main body, head, tissues strong as boron.  12%-}



She had to stop, start again.  Her power did that, if she didn't focus, kept giving her a steady flow of information but not information she could use.



Leviathan had dispatched the three flying heroes and was dueling with Narwhal.  Ballistic from the Travellers was providing supporting fire, sending trash, dumpsters, rubble and pieces of the street careening into Leviathan.



\emph{Another try}.



\emph{Durable layers to body, no conventional organs, irregular biology: Tissues mend from the inside out, layers expanding to fill wounds and integrating into surrounding structures.  Not human.}



\emph{Knew that much}.



\emph{Not human: Never was human.}



That gave her pause.  But she could imagine Grue shouting at her, ``Something we can use!'' and that was nudge enough to get her to focus her efforts.  ``Weak points.''



\emph{No vulnerable organs, hyperdurable tissues: simple organs exist at core of torso, where there is highest amount of surrounding tissues.  Optimal thickness of layer and narrowness of body part at upper arms, just before shoulder joint, and upper thighs, just below hip joint.}



Something she – everyone – could use.  She pressed the button for the communicator on her armband, ``He's got weak points, sort of.  He'll take the most damage at the arm-``



She was cut off by a blared warning from the armband, and a shuddering rumble of the roof she and the squad of ranged combatants had gathered on.  The rumbling only intensified with each passing second.



``Wave!'' someone screamed.



Forcefields went up, and being as high as they were, they were out of reach of the worst of it.  She could see it, a tide of water several stories high.  The impact was reduced to a manageable level  only by the shattered Boardwalk and fallen buildings at the end of the road, the uphill slope.



The crash when when the wave rolled against the side of the building was enough to knock over nearly everyone on the roof.



\emph{Structure, building age, strength of wave; building will hold.}



\emph{Hope the people on the ground are as fortunate}.



Except another problem became immediately clear.  Without the interference of the most durable front line combatants, Leviathan was able to move freely.



The building shuddered, one wall of the building began to crumble, and Leviathan climbed fast enough that his momentum carried him twenty feet above the rooftop.  He landed in the midst of them, and the roof crumbled beneath his mass.  Two people closest to him were swallowed up as the roof disintegrated underfoot, tumbling towards Leviathan.  He adjusted the position of his feet and one hand, to place them at the still-intact portions of the roof's edge, where the structure was strongest.



Only a second after he'd landed, the water that followed in his wake crashed down on the roof, splashing out to push everyone present ten or fifteen feet away from Leviathan, tearing the gaping hole in the roof open even further.  Tattletale gripped the edge of the roof to keep from being pushed over, choked as water forced itself into her nose and mouth.  A less fortunate cape screamed as she fell.



\emph{This would be a good fucking time to act, Regent}.



\emph{Wave; Regent briefly incapacitated.}



``Fuck,'' she muttered.



\emph{Hadn't Taylor been in a situation like this when they'd met?  With Lung?  How had she coped?}



\emph{Right, she hadn't.  We stepped in.  Great.}



The armband was still rattling off the casualties from the wave.  As Tattletale coughed, tried to clear her mouth enough to breathe, Leviathan lashed out with the one claw that wasn't planted against the walls of the building, easily striking two heroes down.  From the damage done, it was painfully obvious that they weren't invincible or anywhere close to it.  A third person gravely injured by the crushing flow of water that followed in the wake of his claw, momentum and a lack of attachment to Leviathan's own body letting it extend well beyond his reach.



Some cape wearing armor studded with stone imagery retaliated, some sort of power that let him generate matter, like chunks of rock or metal pouring out in a stream, spraying into Leviathan's face, making the creature pull back.



Leviathan retaliated with a whiplike lash of his tail, bisecting the man.  Of the twelve or so that had been on the roof a minute ago, only three remained.



Not even looking her way, Leviathan raised one claw in Tattletale's general direction.  The water on the roof shifted, surged toward Tattletale in an isolated wave as tall as she was, lifting her, pushing at her.



The sting of the spray and the salt of the water blinded her.  There was a brief dizzying moment where she realized she couldn't tell which way was up.  She realized she was falling.



\emph{Stupid, }the thought was an accusation, biting, directed wholly at herself.



\blacksquare



She was the last to arrive.  She grinned as she joined the group that had gathered by the entrance to the Trainyards.  \emph{So these are the people Coil found}.



``You aren't wearing a costume, and you're late,'' spoke the tallest of the three present, his voice echoing as if from someplace more distant than he was.  He was covered in darkness that smouldered like a low flame, obscuring him, drifting off in faint wisps.  At times, she could see the image of a skull in the midst of it.  Intriguing.



\emph{Darkness generation; muffles sound.}\emph{ Muffles sound, light: inhibits radiation, microwaves, radio frequencies, miniscule effects on the transfer of kinetic energy-}



``Don't have one,'' Lisa replied, before she could get lost in the flow of information and took too long to respond.



``You'll have to get one.''



\emph{Orders, demands, statements, condemnations, use of skull in costume: solo operator, organized, careful to divorce emotion from action & agenda.  Falls back on order, rules, self discipline in times of stress.}



``I was sort of thinking I'd take a backseat role, serve as your contact, the gal on the other end of the phone, keeping you guys on track, feeding you info.''



``Fuck that,'' the only other girl in the group spoke, jabbing a finger at her, ``If you're taking an equal share, you're gonna get your hands dirty too.''  One of the dogs that accompanied the girl growled, as if to punctuate the statement.



Word choice, `too':  haunted by demons.
Swearing: Antisocial.\emph{ Unhappy with status quo:  seeking to change things, seeking money, power, prestige.}\emph{ Antisocial, swearing, clothes prioritizing function and comfort over style:  not seeking human connections, prefers company of dogs.  Powers relate to dogs.}\emph{ Powers relating to dogs, not seeking human connections, antisocial, inner demons: powers side effects disconnected standard human empathy and understanding, no longer grasps full extent of human relations, signals, signs, cues-}



Tattletale shrugged, admitted, ``My power isn't so good in a direct confrontation.''



``Figure it out,'' the darkness generator told her.



``Alright, can do,'' she assured him.  As much to test his patience and see his limits, she grinned and offered the words, ``Should be fun.''



The darkness generator folded his arms .



\emph{Folded arms: Irritation, doubt.}



She glanced at the one person who hadn't spoken yet.  Hard ceramic mask with a blank expression frozen on it, a coronet set atop black hair, renaissance era clothing.  Only his eyes were visible.



``Barrels of fun,'' the boy spoke, in a tone that might have been sarcastic, or might have been disinterested.  His eyes met hers.



Disinterest or affected disinterest, lack of engagement, lack of pupil dilation or contraction coinciding with eye contact:  limited emotional depth, deeply repressed emotions and/or depression.  Sociopath.



Odd as it was, she felt better, knowing these things.  She liked to think that everyone had roughly the same measure of fucked-up-ness in them, some weird or offensive element.  Knowing that it was so close to the surface, or relatively close in the darkness manipulator's case, it was almost reassuring.  It meant that she didn't find out something ugly days, weeks or months down the line.



Which was a set of memories she was not keen to dwell on.  She pushed that thought & the emotions that boiled up with it out of her mind and grinned as though she found Regent's comment amusing.



The darkness generator made a noise, which she realized was a sigh.  He spoke, ``Alright.  We do this team thing, we're going to do it properly.''



``Of course,'' she smiled wider.  As much to irritate him as anything else, she added, ``How hard could it be?''





