





Coil held firmly to the philosophy that one couldn't be too paranoid.  Every moment of every day was a delicate balancing act, anticipating any number of unseen threats from every possible angle, whether he was speaking with his subordinates or simply rising to meet the day.



In one reality, he was safely ensconced in his underground base, costumed, with no less than twenty armed soldiers between himself and the multiple sets of heavy metal doors.   He had spent his night reading, following the news and checking his stocks.  His location was known only to those who worked for him, individuals paid well enough that even if they did have reason to attack him, their `coworkers' would have incentive to stop them.



Second reality:  He was waking up in an ordinary, slightly rundown home in the southwest end of the city.  He prepared and ate his breakfast, then stepped outside in his bathrobe to pick up the paper and the mail, pausing to wave to the neighbors as they led their two girls out of the house.  The flooding hadn't affected their neighborhood as much as others, but the schools weren't yet up and running, so the mother and father would be taking their girls to work with them for a short while.



He headed back inside, showered, then dressed in a button-up shirt, khakis and a silk tie.  He got in his four-year old prius and headed into the city.  What was normally a ten minute drive took him three-quarters of an hour, as he was forced to detour around destroyed roads, fallen buildings, and reconstruction work, move with the other drivers in a perpetual traffic jam from the moment that he left the little cul-de-sac where his house was.  To all appearances, he was an ordinary man leaving for work.  His identity, fabricated, was complete, a real job at a real company, records going back ten years in health, taxes, dentistry, house payments and more.



The soldier that met him was known to the other soldiers as Creep.  No captain would have the man in their squad, his predilections made him unemployable in the public sector, and the fact that Coil was the sole person who could and would provide him with the `payment' he craved makes Creep as loyal as men can get.



Everyone had a hook, a vice or something they needed on a primal, desperate level.  Sometimes that need needed to be created, or nurtured, so it could later be hand fed.  Those people who were driven by such things, carried that craving for something especially close to the surface, were among Coil's favorite people, coming in a very close second to people who were \emph{useful}.  Those who were both useful \emph{and} desperate for something Coil could provide?



Well, they were the Travelers, Creeps and Grues of the world.



Wealth would have to suffice for anyone and everyone else.



Creep remained the one individual that had the opportunity to discover Coil with the mask off, so it was worth buying his loyalty.  The man waited in the front seat of the white van, eyes forward, until he heard the three knocks on the back door of the vehicle.  He pressed a button, opening the door to allow Coil to enter.



Once inside the back of the van, hidden from Creep's view by a barrier between the seats, Coil removed his clothes, folding them neatly.  He donned his costume, his second skin.  A zipper was hidden in the image of the long white snake that weaved up around the body of the costume to the head.  He drew it together around himself, tucked the metal tab of the zipper into a flap at his ankle. The fabric of the costume allowed him to see and breathe through it, but was an opaque black-gray to outside observers in all but the brightest light.



He was spending less and less time in his civilian identity, these days, to the point that he was pondering dropping it altogether.  He could be Coil full-time, when the base was fully set up.  For now, though, so long as he needed a bed, and a place to get away from the noise of construction, the ruse was necessary.  He seated himself in the one chair at the back of the vehicle.



To outside observers, Creep was an ordinary laborer driving an electrician's van to the construction site.  Coil's underground base had fallen just beyond the scope of the massive lake in the middle of downtown.  Had the crater extended another forty or fifty feet, it might have done more than crack the interior walls, cost Coil months of time rather than days, hundreds of thousands rather than thousands.



Creep directed the vehicle down the ramp and into the parking garage.  He stayed behind with the van as Coil departed.



Coil entered a doorway in the lowest, most secluded corner of the parking garage, entering a room with an electrical system behind a metal cage.  Opening the door to step into the cage, passing around behind the electrical box and passing through the concealed doorway there, he reached the heavy vault door that marked the entrance to his underground base.



Even after he was inside, with two employees waiting to greet him, a contingent of his squad captains standing at the ready, he remained careful.  Back in the other reality, he stood from his computer, traveled into the room beside his own.  He paused in the doorway, staring at the girl who lay on the cot.  She was dressed in white, unmoving but for the rise and fall of her ribcage, her eyes open.



``It's morning, pet.  You know what questions I ask you.''



``It's morning?'' she asked, head rising.  ``I feel like I just had dinner.  Candy?''



``No, pet.  It's too early.  Now please answer my question.''



Petulant, she replied, ``Zero point two five two percent chance there's any problems here in the next hour.  Three point seven four four one percent chance there's any problems before lunchtime.''



``Good girl,'' he spoke.



With that, he collapsed that world where he had stayed up all night, studying the news, following international business trends, tracking the details on his troops' most minor operations – he helped ensure the success of the major ones with his power.  The reality swiftly faded, leaving only the world where he had a full night's sleep, ate a hearty breakfast, drove to the base with Creep.  Only the memories and knowledge remained.



Standing before his employees and soldiers, he divided realities once more, leaving only a heartbeat between the erasure of one existence and the creation of another.



He often wondered if he really was creating the realities, or if it was solely in his perception, foretelling futures to the extent that they hinged on his actions.  He'd asked his Tattletale, and she hadn't had an answer for him.



He had hated these moments, before he'd acquired his pet and the assurances she provided.  These were the times when he was most vulnerable,  when he'd just started a fresh use of his power, his selves so close to one another.  It was sadly inevitable, unless he found a way to expand to a third world.  Though he knew the chance of danger was miniscule, that his pet could not lie to him if she had wanted to, he still made efforts to distance the two worlds as much as possible.



The first reality: ``Captains, with me.  Empire Eighty-Eight is divided, and I'm going to direct you on a series of strikes to ensure we deal as much damage as possible before the two factions can merge once more.''



The other: ``I wish to survey the base.  Captains, as you were.''



Two groups traveling in separate directions.  One of his selves traveled with the troops, down the metal staircase to the lower level, the other moving in the other direction, across the metal walkway, the two employees hurrying to keep up with his long strides.



He eyed the base as it was developing.  The massive quantities of crates and boxes were being unpacked, bunk beds for soldiers on call, a fully equipped medical bay, stocks and facilities for the kitchens, innumerable weapons.  It was taking shape, fine details emerging where there had been only right angles and neatly organized stacks boxes.



He owned the company that had built the underground shelters in Brockton Bay and neighboring cities.  Hiding the details on his base in construction was a matter of intercepting information at the right time and place, paying with his own money rather than the city's, controlling what was reported and to whom.  His pet's powers had assured him that nobody would be noticing any disparity anytime soon.



``The Travelers' room,'' it was more statement than question, but it required an answer.



A man in a sweater and small round-rimmed glasses, Mr. Pitter, spoke, ``Done.  Individual rooms, furnishings, kitchen and wardrobes.  Some minor modifications are needed to make it more handicap accessible, but they could all move in today.''



``And the containment facility?'' he asked, though he already knew the answer, from the interruptions while he spent the night in the facility.  He'd heard the noise of the work just hours ago, been informed that people were arriving.



``The vault door was placed just last night.  She was--'' Mr. Pitter paused, ``Agitated.  We had to call Trickster in to talk to her.  He's here now.''



``I'll speak with them.''



``Yes sir.''



He didn't like interacting with people, especially not subordinates as important as the Travelers or Undersiders, without the ability to create or banish the reality if the discussion didn't go his way.  Here, he was safe.  His other self was giving orders on movements, targets to attack, individuals to watch out for, informed by the night he had spent tracking the deployments and patrol patterns of the Protectorate and Wards.



He let Mr. Pitter take the lead as they headed to the Traveler's apartments.  The man was small, unassuming, ordinary.  A registered nurse, he had an exemplary eight-year record of acting as nanny and caretaker to a pair of very ill children.  Then he had found out his wife had cheated on him, attempted to divorce her.  Deciding that wasn't acceptable to her, the woman had set about dismantling his life, ruining his careers, friendships, familial relationships and everything else, laying accusations and planting evidence of the worst sort of crimes.  The sort of accusations and suspicions that a male nanny had to be leery of at all times.



Mr. Pitter was one of those particular people who was both useful and bought with stronger things than currency.  He would ensure the Travelers were comfortable and well stocked.  More specifically, he would take care of Dinah, ensure any and all dosages were clean and properly administered, that the girl was kept in the best of health.  All he had required was for his wife to disappear, the chaos and problems the woman had caused him discreetly sorting themselves out in the aftermath of her death.  He had gone from being a broken man to a person who was so unflinching in his duties that it had given even Coil pause.



Mr. Pitter knocked on the door, waited.  It was almost a minute before it opened.



Trickster stood in the doorway, unmasked.  His skin tone was darker in a way that left his ethnicity ambiguous, to the point where the boy could have been a darker skinned Caucasian, biracial, Middle Eastern or Eastern Indian.  His dark hair was long, hanging to his shoulders, and a hook nose coupled with a widow's peak gave him something of a severe appearance.  His eyes, normally sharp, were bleary with sleep.



``Are you really that sadistic, Mr. Pitter?  I get dragging me here at five in the morning if Noelle needs it, but waking me up three hours later?''



The `nanny' didn't reply, instead stepping out of the way, to give Trickster a better view of Coil.  Trickster leaned out of the doorway to look his employer up and down, picked some sleep from the corner of his eye with his thumbnail.  ``Damn it.  Okay.''



``Thank you,'' Coil replied, ``I would like to speak with your friend, downstairs.  Past experience has suggested this works best if you act as an intermediary.''



``I don't know if that's a great idea.''



``Indulge me.  Would you like me to wait while you wash your face?  Get dressed?''



``If we're just going to talk to her, and if you don't have anything else for me to do, I'll probably go straight back to bed, after.''



``As you wish.''



Trickster pulled on a black bathrobe, cinched it around his waist, then stepped onto the metal walkway.



``Is there at least anything I can tell her?'' Trickster asked.  ``Anything encouraging?''



``Nothing definitive.  I had intended to introduce Tattletale from the Undersiders to this situation, ask her for her opinions.  That is, if she doesn't already have some idea of what's going on.  Either way, her talents might turn up some details we have missed.''



``Had intended?  I take it that she can't, now, because of what happened at the hospital?''



``Something like that. She's informed me that there's currently difficulties within her group and requested that I not distract her or give her tasks until things have been settled `one way or the other'.  Her words.''



``That's not really anything that's going to give Noelle hope.''



``No.  No it isn't.''



They headed back onto the walkway, then down the stairs.  A vault door, twenty feet across, was set into the concrete wall.  It loomed over them, three times as tall as even Coil was.



Coil stepped to the side, gestured toward the small monitor and keypad to the left of the door.



Trickster touched a button on the keypad, ``Noelle?  You there?''



The monitor flickered.  A girl's face took up most of the screen.  Her face was framed with brown hair, greasy, and she had dark circles under her eyes.  Her eyes moved as she looked at the monitor on her end, but she didn't reply.



``Hey,'' Trickster spoke.



``Hey,'' her voice had a ragged quality to it, as though she had screamed herself raw.



``Coil wants to speak to you.''



There was a pause.  ``Okay.''



Coil stepped forward so he shared the camera with Trickster.  ``Noelle.  I'm sorry the construction work disturbed you.  We shouldn't have been doing that so late in the night.''



``You locked me in,'' Noelle accused him.



``For your safety, and ours,'' Coil spoke.



``You agreed to this,'' Trickster told her, ``We talked about it.  You \emph{asked} us to do this.''



``I know.  I-  I didn't think it would be this claustrophobic.  Or lonely.  I swear I'm getting cabin fever and it's only been a few hours.''



Trickster opened his mouth, then closed it.  When he finally found the words to say, he spoke, ``You can call me any time.''



``Except when you're doing a job.''



``You can talk to Oliver, then, or Mr. Pitter.''



``Oliver's still busy talking to you guys, and Mr. Pitter creeps me out.''



Coil raised an eyebrow behind his mask, gave Mr. Pitter a glance.  The man hadn't reacted.



Trickster diplomatically didn't comment on Mr. Pitter's presence nearby.  Calmly, he spoke, ``We're working on a solution.''



``You've been working on that for a month now!''  She began to shout, which only added to the gravelly quality of her voice, ``Fix this!  Fix me!  \emph{You did this to me, }Krouse\emph{!}''



``Noelle,'' Coil spoke, controlling his voice, ``Trickster is not to blame.  At the next possible opportunity, I will be inviting an employee of mine to speak with you and the rest of the Travelers.  Her power will provide hints.  I've also been in contact with the head of parahuman studies at Cornell.  An expert in the field.''



Her scream sounded through the intercom system, ``That's just more poking and prodding and theories!  You \emph{promised} us you'd fix me!''



Punctuating her statement, there was a bone-rattling impact against the vault door.  Almost every soldier on the lower level stood or turned to face the doorway, hands on their guns.  Dust spilled out  from the joins where the concrete walls met ceiling.



Irritating.  Nothing more was going to come out of this conversation.   At least he knew the one thing he'd sought to find out: she was getting worse.  He used his power, obviating the reality with the raging girl in favor of the one where he was talking to his soldiers.



``--dersiders are otherwise occupied, so you'll be supported indirectly by the Travelers.  Captain Heroux?  How fast can your squad be ready?''



``We're ready to go at a moment's notice.''



``Good,'' Coil spoke.  ``Be ready, I'll have orders for you in less than an hour.''



``Sir.''



Coil turned, leaving the captains to their assigned tasks.  He glanced at Mr. Pitter, ``The Travelers' quarters are all set up, I trust?''



``Yes.  We just installed the heavy door in the middle of the night.  Noelle was agitated enough that we had to call in Trickster to calm her down.''



``I see.''



``He's still here, if you want to talk to him.''



``Let the boy rest.  He'll be tired.''



``Yes, sir.''



``Ensure the girl has a double ration for this morning.''



``The costs--''



``Are my concern.  With her sleep disturbed, she is liable to be\ldots cranky.  Let's ensure she has little to complain about.  And Mr. Pitter?'' he paused, ``Speak with Duchene about the construction the second she comes in.  I want that door on the lower level reinforced.  Extend walls inward and put in a second door, if you have to.  Schedule any construction for the middle of the day, so we aren't interrupting her sleep again, but I want it done as soon as possible.''



The man nodded, correctly interpreted the order as a dismissal, and hurried off.



That left him with the one remaining assistant following after him.  Cranston.  ``Anything urgent?''



``No, sir.  The businesses you purchased are still struggling in the wake of the catastrophe, but we've received insurance payments--''



``Good.  We'll discuss it later.''



``Yes, sir.''  Cranston hurried off.



Coil returned to the end of the complex furthest from the entrance, entered his quarters.  He paused at his computer to check his emails and the latest news feeds.  Nothing crucial.



He divided realities.  In one, he stayed at his computer.  In the other, he entered the room reserved for his pet.  ``Good morning, pet.''



``It's morning?'' she groaned, sitting up.  ``I thought I just finished dinner.  Candy?''



``You know my morning questions.''



He already knew the numbers – he noted they had barely changed, as she rattled them off – but if he always canceled out the reality where he asked her for the chance of any danger in the morning and never asked again because it would be redundant, she would never remember.  Even a mind like hers had its limits and boundaries.



``The chance my grand plan is a success, ignoring any uses of my powers?''



``Seventy two point two zero zero two one percent.''



Pleasing.  It was a number he could raise in the ensuing days and months with the use of his power.  Interestingly enough, the number was\emph{ better} than it had been before Leviathan attacked.



``Chance the issues with the Undersiders will be resolved?''



``Don't understand.''



He frowned.  Another limitation.  She needed to be able to visualize the scenes.  ``What is the likelihood that the Undersiders will still be serving under me, at the point in time my plan succeeds or fails?  To one decimal point?''



``Sixty five point six.  But they aren't all the same Undersiders.''



``Oh?'' he rubbed his chin, ``The chance that my plan succeeds with this new group versus the old?''



``I don't understand.  My head's starting to hurt.''



``Just one or two more, pet.  If the group changes, is it more likely that my plan succeeds?  To one decimal point.''



``Yes.  Four point three to eleven percent, depending on who comes and who goes.''



``One more question.  What is the chance that I find a remedy to the Travelers' circumstances?  To one decimal point?''



``Nine point five.  Candy?''



A full seven percent lower than it had been before the Endbringer attack.  Had a crucial individual died or left the city?  Or was his running theory correct?  Was there a reason Leviathan had come here, beyond the chance to attack a city already under siege?



It was hard to ignore the reality, that Leviathan, from the time he arrived, had gradually moved closer and closer to this location, where the girl had already been ensconced.  The Travelers had even picked up on that, called him, worried.



Something to ask Tattletale about, perhaps, when he introduced her and Noelle.



``It feels bad.  Wanting the candy so much, knowing I'm \emph{going} to want the candy, seeing it like I do.  It builds up.''



Seven percent lower.  At what point did earning their loyalty fail to be worth the resources he was investing?



``Knowing I'll get sick if I don't get it, being able to see it, what it's like, the getting sick, and as it gets closer to happening, higher percentages, it feels more real, so clear a picture it's almost as bad as getting sick for real.  Even if there's only a nine point two--''



``You'll get some to tide you over in a bit, pet,'' Coil interrupted her, in as reassuring a tone as he could manage.  It was impossible to conceal all of his irritation at being disturbed from his thoughts, but she was distracted enough by her own problems that she likely didn't notice.



His plan was succeeding, though it had been delayed slightly by recent circumstances.  Potential enemies were divided or reduced in numbers, the city all the more vulnerable to being seized.  Victory was so close he could taste it.



Perhaps worthy of a celebration.  Coil maintained his own vices.  It would be unfair to expect more of himself, when he had the unique talent he did.



It had certainly been an \emph{expensive} talent.  Even with his ability to game the markets in a way that clairvoyants and precognitives couldn't detect, it had taken him years to pay it off.  A maddening, frustrating endeavor, when he had already been thinking of plans he wanted to set in motion, having to postpone them.  \emph{And} he still owed a favor, even now, up to a week's services.  He couldn't be sure if he was powerful and secure enough to fight back if they demanded too expensive a price, or too much of his time at a point critical to his plan.



He canceled the reality where he stood at his pet's bedside, found himself still at the computer.  Best to leave the world where his pet wasn't so tired, in case he wanted to ask more questions that morning.



The worlds he created weren't real.  They were little more than an especially vivid, accurate dream.  To enjoy a whole separate world, free of any consequences beyond the ones he wanted?  It would be unreasonable if he \emph{didn't} indulge in it.  Anyone would, given the chance.



These entertainments kept him centered, utterly calm.  He needed that, after the irritation of dealing with the Travelers' girl.



He touched a button on his phone, ``Mr. Pitter?  My office.''



``Yes sir,'' the reply sounded.



He was on the brink of achieving his goals.  It would be a laughable tragedy, to get this close, only to have his power fail him, to accidentally choose the wrong reality, or to have his other self killed by accident or malicious intent, forcing him to live with the ramifications of these idle amusements.  For now, he wouldn't touch his pet, nor any of his powered subordinates.  Not when he was this close.



A click of what appeared to be a part of his desktop wallpaper made his bottommost drawer pop open.



Mr. Pitter entered the room.  ``Sir?''



One reality: ``My pet needs her `candy', a low dosage, please.''



The other: Another click of his computer mouse, remotely locking the doors.  Mr. Pitter turned, alarmed, tested the door.



For now, even with the safeguard of his other realities, he would do nothing he couldn't explain away if he had to.  He wouldn't entertain himself with anybody he couldn't replace.  Mr. Pitter?  Replaceable.



No such thing as being too paranoid, after all.

