





The empty vault loomed before us, dark and fetid.



``It's that bad?'' I asked.  ``Do we need to contact the PRT and Protectorate?  Get the heroes on board?''



``No,'' Dinah said, quiet.  ``Not immediately.''



The others looked at her.  I couldn't see her, but I had a pretty distinct mental picture.  A pre-adolescent girl, thin, with straight brown hair.  Cursory inspection with my swarm suggested her hair was tied into a braid, but many strands were coming loose.  Unless a lot had changed since I'd last seen her, Dinah would be pale.  My mental picture of her was of a girl that was almost \emph{ghostly}.  It said something that she was still able to command our attention with a few quiet words.



``One point seven percent chance she does any serious damage before dawn.  We have time.''



``Thank you,'' I said.



``Useful to know,'' Tattletale said, ``But this is bad enough that we may have to go running to the heroes, eat crow and ask for their assistance, get it sooner than later.''



Regent had followed Grue, Dinah and I down the stairs.  He peered into the darkness, then said, ``I don't think we'll have much pull with the white hats.  Among other things, we've conquered the city, gave their heroes a series of spankings, gave the world-reknowned \emph{tinker} a \emph{very expensive} spanking, kidnapped one of their Directors and if I just heard you right, you just offed the \emph{replacement} director.''



He stepped back, moved his mask and whistled.  I had to step back to see Rachel on her way from the entrance, her dogs following behind.



I couldn't help but cough at the rancid smell from the vault, which made me cough \emph{more}.



``Hospital,'' Grue said, for the umpteenth time.



``Soon,'' I said.



``The heroes don't know we offed Calvert,'' Tattletale said.



``Yet,'' Regent added.



``My question stands.  Do we need to contact them?'' I said.



``Maybe.  I don't know,'' Tattletale shook her head a little.



``What \emph{do} you know?'' I asked.  ``Because as far as the rest of us are aware, there's a teenage girl that's capable of tearing through two vault doors like they're nothing, and she's free, \emph{and} she's pissed at us.  Quite possibly at \emph{me}, depending on how much she heard.''



``Coil sent the Travelers to me for help.  She's had some physical changes,'' Tattletale said.  She traced one of the creases in the crumpled vault door with her gloved fingers.  ``They wanted to get a better idea of what was going on, so they could maybe change her back.''



``And when I asked about her before, you brushed me off.''



``Don't like admitting I don't know something,'' she said.  ``And I don't know the full story.  \emph{They} were working on the assumption that she's turning into an Endbringer.''



That gave us all a moment's pause.  Rachel had just descended from the walkway in time to catch the last part.  She grabbed Bastard's chain to keep him from venturing into the vault, but her attention was on Tattletale.



``\emph{Seriously?}'' Regent asked.



``No.  Well, it's what they were thinking.  It's not what I think.''



``Elaborate,'' Grue said.



``When I saw Leviathan, I got the distinct impression that the Endbringers aren't human and \emph{never were}.  Noelle?  She's human.  So I've got two running theories.  Theory one is that she \emph{is} turning into an Endbringer, with her body serving as the host to a growth that's eventually going to shed off the \emph{Noelle} bits and go full-monster.''



``And theory two?''  Grue asked.



``Someone's doing their level best to make their own Endbringer.''



``Who?'' I asked.



Tattletale shrugged, ``No clue.  Could be any of the major players.  To figure out which one, I'm going to need time with the database on capes we downloaded from the PRT.  Even then, I'm not sure it covers the high-clearance stuff we need.''



``Off the top of your head?''  I asked.



``Who could it be?  The Protectorate might have been aiming to make an Endbringer with the idea that it could fight the other Endbringers, only for things to go sour.  There's the group that made people like Gregor the Snail and Newter,'' Tattletale looked at me, ``You remember that paperwork we found when we infiltrated the Merchant's party.''



``Cauldron.''



``Yes.  There's also any number of megalomaniac tinkers out there who might have tried something. Bonesaw, Rattenf\"{a}nger, Jamestowner, Blasto, Mosaic, Monstrum, some non-tinkers like Chrysalis and Nilbog, bunch of others.''



``Too many,'' Grue said.



``But their powers don't fit this scenario that well, so it would have to be some alliance between two of them, or one would need to get ahold of the tools and blueprints from one of the others and reverse engineer it, \emph{or} one had a second trigger event and their powers expanded.''



``A lot of `ors','' Grue said.



``Too many possibilities,'' Tattletale said.  ``We could be\emph{ }on the complete wrong tack, where I'm overthinking it, or I'm overlooking the most obvious possiblity, that she's just unlucky.''



``What if we ask the kid?'' Regent asked.  He turned his attention to Dinah.



``Only if she's up to it,'' I said.



``Head hurts, still fixing things, putting all the worlds in the right places,'' Dinah said.  She was clutching my wrist as though I were a life preserver and she was going to drown if she let go, but she stared at the ground as she spoke.  ``But I'll help now.  I fear I won't be useful for much longer.''



\emph{I fear?}  Who talked like that?



``Why not?'' Regent asked.



``I'll get sick without the candy.  Soon.''



``Withdrawal,'' Grue said.



Dinah nodded.



``Fuck,'' I said.  ``We need to get her to a hospital so they can see her through it.''



``I can see it,'' she said, and her voice was smaller.  There wasn't any inflection when she spoke; the only indication that she had any emotion at all was the changing volume of her voice, more volume as she got more confident, less as she drew into herself.  ``I see myself getting sick, and it's so clear a picture, so \emph{many} pictures it's almost as bad as being sick right here and right now.''



``There's ways they can help you through it,'' I said.  ``I looked it up.  The hospital can put you under, so you're not awake for the worst of it.''



She squeezed my wrist a little tighter.  ``It's okay.  I can see the chances and I know I'll be okay.  So long as it's just once.  Ask me questions.''



Tattletale glanced at me.



``Go ahead,'' I told her.



``Chance she's turning into an Endbringer?'' Tattletale asked.



``Those aren't the kind of odds I can give,'' Dinah said  ``It has to be something I can picture.  Scenes.''



``I thought so.  And that'd mean I can't really use it to pin down who's behind Noelle's situation.''



Dinah shook her head.



``Chance of trouble in the next twenty four hours?'' I asked.  ``Violence, she attacks us, she attacks other people\ldots''



``Ninety-nine point three four six three zero one percent,'' Dinah said.



``What happens in that not-even-one-percent chance?'' Regent asked.



``I can't go looking.  I have to ask, and figure it out from there, which hurts if I do it too much, or someone else asks, which makes it hurt less, because I can focus on the numbers and just the numbers.''



``Okay,'' Tattletale said, ``Chance she runs? ''



``Twenty-three point three one one percent.''



``That doesn't add up,'' Regent said.  ``Unless I'm way worse at math than I thought.''



``She does some damage and then flees,'' Grue suggested.  Tattletale nodded confirmation.



``Chance someone stops her?'' Tattletale asked.  ``Defeats her, kills her?''



Dinah shook her head.



``You don't know?''



``I can't see it.''



``Okay,'' Tattletale said.  ``That means we probably can't stop her with sheer firepower.''



``Didn't see it.''



``Okay.  Thank you, by the way,'' Tattletale said.  ``Appreciate it.''



``You're quite welcome,'' Dinah said, dropping her eyes to the ground.



\emph{Quite welcome}.  Dinah kept phrasing things in a funny manner.  An old fashioned or \emph{proper} way.  It wasn't quite like how Coil spoke, but there were similarities.  Was it a side effect of spending \emph{way} too much time around Coil?



I didn't like the idea of that.  That either Coil had molded her, or that she'd spent enough time in a pliable mental state that she'd adopted his speaking patterns.



``This situation is bad,'' Tattletale said.  ``We can't take her on, but we don't know enough about her to plan against her.  I was going to reposition everyone so our territories covered the entire city, under the assumption that the Travelers were leaving.  Now I'm suspicious they'll be staying, which complicates matters, and I don't want us spread too thin, either.''



``We could get hold of Ballistic,'' Grue said.  ``Get his version of events.''



``He went back to his territory.  I'll make calls and see if we can bring him on board,'' Tattletale said.  ``I have two squads of soldiers that I'm keeping on retainer.  They'll serve as my hands for right now, while I try and get myself sorted out here, establish this as my new headquarters.  If you guys want to go to the hospital, maybe see about getting Skitter and Dinah looked after, I'll handle things on this end.  We regroup at least an hour before dawn and we plan with whatever new information we have.''



``No sleep tonight?'' Regent asked.



``No sleep,'' Grue confirmed.



I turned to Tattletale, ``We don't have access to all of Coil's resources, now.  Or Calvert's, for that matter.  Can you find us a doctor who we can trust?''



``Someone you can trust?  No.  But I can find someone not altogether \emph{un}\emph{trustworthy.}''



\blacksquare



We were just finishing sorting out who was going where when Tattletale called us with a name and an address.



The group heading to the hospital consisted of Me, Grue, Rachel and Dinah.  I had the smoke inhalation and breathing problems, as well as the pain in my chest and my eyes to look after.  Grue and Rachel had been shot.  As for Dinah, we needed to make sure there weren't any severe problems before we sent her home.  Regent headed back to his place with Imp for backup.



Dinah, Rachel and I settled in the back of one of Coil's trucks with Bastard and Bentley.  Grue took the wheel.



I focused on canvassing the area with my swarm as Grue drove.  Dinah had assured us that things were safe for the rest of night, but I couldn't ignore the existence of a dangerous pseudo-Endbringer with a very good reason to want to hurt me.



``\emph{You're} quiet,'' Rachel said.



I turned my attention to her, then realized she was talking to Dinah.



``I considered saying something, but you would get upset,'' Dinah said.  Again, the low volume.



``Huh,'' Rachel said.  ``Why?''



Dinah paused for long seconds.  I wondered if she was trying to work something out with her power.  ``I was going to ask if I could pet your puppy, but it's\ldots not my place.  He's not mine.''



``He's not a dog.  He's a wolf.  He doesn't react like a dog will.  And I'm trying to train him before he's old enough that he won't listen, and I don't need people mucking that up.''



``Okay,'' Dinah said.  There was no fight there, no resistance, total compliance.



Rachel put one boot against the edge of the bench across from her, a foot to the right of Dinah.  As far as I knew, Rachel didn't take her eyes off the girl.



``Rachel,'' I said.  ``Just curious, but you're hoping to eventually adopt your dogs out, right?''



``To good owners.  So?''



``Just saying, but as much as the owners need to adapt to the dog and understand the dog, the opposite is true.''



I couldn't read Rachel's expression.



``The dog has to adapt to the owner?'' She asked.



``Right.  And that means the dogs need a chance to get used to people.  Dogs and humans have a partnership, right?  So they need to meet halfway in that understanding.  \emph{Mutual} understanding.''



``Okay.''



Enough time passed that I wasn't sure if she'd picked up on my meaning.



``You want to pet Bentley?'' Rachel offered.



``Very much,'' Dinah replied.



``Bentley, go.  Up.''



Bentley hopped up between Dinah and I on the bench.



``Relax.''



The bulldog turned around once, then flopped down on the bench so his head was pressed against my hip.



``Give him a sniff of your hand before you touch him,'' Rachel said.  ``Bentley's a good boy, but it's a good habit to get into with dogs.  You don't want to surprise him and get bitten.''



I kept still while Dinah took Rachel's suggestion and extended a hand.  Without standing, he twisted himself around until his oversized head was in Dinah's lap.



\emph{Months since she's seen a dog, let alone touched one}.  How would that affect her in the long run?  I hoped she wouldn't be in therapy for the rest of her life.  I turned my attention to scanning the area, while Bentley reveled in the attention and affection.



It was another five minutes before Grue stopped the van and we had a chance to get out.



``Chance of trouble?'' I asked.



``Fifteen point three three percent,'' Dinah answered.



``Can you tell me who causes the trouble?''



``I only know \emph{we'll} be in there, so I have to look at each of us, one by one, and then I see the number.''



``Okay.''



``When there's trouble,'' she said, ``It's you.  Eighty percent of the time.''



``Me?'' I asked.



She nodded.



``Okay,'' I said.  ``I'll try to be good.''



With `Doctor Q', the man Coil had always referred us to, it had been one man operating solo.  He'd known his stuff.  But he'd been Coil's man, and we couldn't trust him until things had time to settle down.



\emph{This} doctor's office had a staff, and they didn't even react as we entered.



``What do you need?'' a woman asked.  She had a musical voice that was almost irritatingly sweet.  Condescending, like a kindergarten teacher or a character in a show for very young kids.  Not to the point that I saw myself causing any trouble, but\ldots yeah.



``Three of us took gunshots, but they didn't penetrate.  Costumes stopped the hits, but I want to be sure there isn't lasting damage,'' Grue said.  ``The little girl needs a full checkup and maybe a brief stay, while she suffers withdrawal from some unspecified drugs or drug cocktails.  And we've got one case of smoke inhalation coupled with severe chest pain.''



``Understood.  Your bill has been paid in advance.  My mother and I will be looking after you,'' the young woman chirped.  ``Please come this way.''



We followed.  The place was like any old doctor's office, but I noted statues and innumerable picture frames, and the floor was tiled.  Going by my swarm sense alone, I got the impression the place was upscale.  And it was empty.



``You don't seem bothered to have supervillains coming through.''



``We've dealt with supervillains before,'' she said, and the way she said it suggested she didn't plan on elaborating.  ``You'll need to remove your costumes and masks.  You can each have a separate room to disrobe, and we'll be seeing each of you in turn.  Rest assured, your privacy and safety is our top concern.''



I could feel Dinah's deathgrip on my arm.



I bent down and murmured, ``Do you want a separate room?''   She shook her head.



I straightened and told the woman, ``We'll share a room.''



``Neither of you are bashful?''



``I'm blind,'' I said, ``And no, I guess I'm not bashful.''



``Blind?'' Grue said, his head snapping around as he looked at me.  Rachel did as well.



``Tattletale didn't mention it?''



``No.  And \emph{you} didn't either.''



``I'm functioning.  I probably won't when I can't use my power, but yeah.''



``Is everything all right?'' the young woman asked.



``It's fine,'' Grue said, heading into one of the rooms.  He stopped in the doorway, turned to me, ``We'll talk after.''



I bobbed my head in a nod, then led Dinah into an empty room.  As far as I could tell, everything was as one might expect for a doctor's office, down to the jar of tongue depressors and a bowl of lollipops.



``How's your head?'' I asked.  ``Headaches?''



``Getting worse.  But I'll get sick tonight, before the headache gets too bad, then it won't really matter.''



``Oh.''



``Do you have more questions?''



``Some, but I don't want to burden you, or make you feel like I'm using you.''



``Go ahead.''



``The end of the world.  Did Coil ask about it?  Did he get more details on what happens?''



``He would ask how the number changed, some mornings when he asked the usual questions, before Crawler came and I couldn't use my power for a while.  He wanted to figure out what happened, but the only way to do that was to make guesses and see the numbers with my power.  Every day, he'd always asked the same sorts of questions about whether one thing was safe or whether another was safe and chance of success for this plan or that.  There weren't many questions left for the day after he was done asking all those, so it was slow.''



I worked to take off my armor, unstrapping the armor to uncover the zipper.  It wasn't easy, with the pain in my chest, and when it hit me, I'd have to suppress coughs to continue listening to Dinah.  ``I guess he figured he'd be around long enough to figure it out.''



Dinah didn't respond.



``What's the chance the world ends, Dinah?  That these billions die because of something Jack Slash does?  Has the number changed?''



``It's changed.  Ninety-seven point seven nine zero seven three percent.''



\emph{Ninety-seven point eight.  It's higher}.



``What did you and Coil figure out?  In terms of twenty questions?''



``People are spread out.  I know \emph{you're} there.  You're different but you're there.''



``And the others?''



``Sometimes there.''



``Can you give me more details?  How am I different?  Which of the others are there?''



``I don't know.  There's too many capes and too many capes with powers that make it fuzzy, because some powers make it harder and a bunch of those powers together make it impossible.   I don't know what happens to start all of it and I don't know much of what happens \emph{during}, but billions are dead afterward.''



\emph{Damn}.  ``Okay.  You said we're spread out?''



``Yes.  Five big groups, lots and lots of capes from all around the world, and armies.  Coil asked a lot about that.  He wanted to know about his chances for survival or the total number of casualties if he focused on one area over another.''



``He wasn't interested in stopping it?''



``He asked about that at first.  But nothing changed the numbers enough.  He said it was better to accept that it's going to happen and do what he could to minimize the damage.''



``Five major groups,'' I said.  ``You don't know why?''



She shook her head.



``Do you know if it's like, a natural disaster sort of mass-death, or death by violence, or\ldots''



I trailed off.  Dinah was already shaking her head.



``Alright,'' I said.  I finished pulling my costume off, grunting at the pain in my chest, then sat on the bed in my bike shorts and tank top.  Dinah sat beside me.



She looked up at me, and there was a hint of surprise in her voice.  ``You're burned.''



``Yeah.  Just a bit.  Is it bad?''



``Not bad.  But it looks painful.''



``My chest hurts more,'' I said.  Then, as if I were reminded of it, I coughed, hoarse.



We sat.  I could sense the Doctor talking to Rachel, and `heard' Rachel's raised voice with the bugs I'd placed on her.  I didn't envy the doctor for having to deal with her as a patient.



``Theoretically speaking,'' I said, ``Just in the interest of problem solving, or figuring out what's going to work or not, would the chance of this happening change if I just drove around America and killed everyone in my power's reach?''



``Not really,'' Dinah said.



``Damn,'' I replied.  If she'd said \emph{yes}, I could have narrowed it down to maybe the eastern United States or the west, then cut it in half again with north versus south, or narrowed it down to certain states.  Home in on the person or people that the problem centered around, dealt with them one way or another



Except that wouldn't work.



``Would you?''



``What?''



``Kill all those people, if you had to?''



``No,'' I assured her.  ``I'm not that kind of villain.''



``You killed Coil, didn't you?  I saw.  Thirty-two percent chance it was you who did it.  Five percent chance you couldn't and asked someone else to.  Sixty percent chance you were dead.''



``I killed him,'' I admitted.  ``But that was a special case.''



``Okay,'' she said.



What I wouldn't have given to be able to read her expression.



``Does that bother you?'' I asked.



She shook her head, but she said, ``It did at first, when I first saw that possibility.  But I had a lot of time to wait, and eventually the idea of being rescued mattered more than his life did.''



``That's\ldots pretty grim,'' I said.  I didn't get a chance to say more.  The female doctor was leaving Rachel's room, and Rachel was storming out.



Both Dinah and I turned toward the door before the doctor had even touched the handle.



The woman entered and hesitated a fraction when she saw us staring.  Her voice was just as cheery as her daughter's.  ``Hello!  I'm Dr. Brimher.''



``Hello,'' I said.  ``Have trouble with my teammate?''



``She was uncooperative.  I suppose we'll have to refund the amount that was already paid for her care.  I hope that's alright.  Everything indicated she was fine, healthwise.''



``So long as she was fine.''



She perked up a little at that, ``Well then!  Who's first?''



``Her,'' Dinah said, before I had a chance to speak.



The overall checkup went much as I'd expected.  I was diagnosed with a fractured rib, the smoke inhalation was apparently something that should have been treated earlier, but I wasn't showing any lingering signs of mental or personality changes, and I wasn't dizzy, so she let me off with instructions to breathe deep.  I got a cream for my burn and three bottles of eye drops for my eyes.



``Once every two hours,'' she said.  ``And as for you, little miss, you seem undernourished.''



``I haven't had much of an appetite for a while.''



``Infection?''



``Involuntary incarceration,'' I said.



``Ah.  Well,'' the woman's voice jumped up a notch on the cheeriness scale, ``None of my business.''



``It wasn't me,'' I said.  ``\emph{We} weren't keeping her prisoner.''



``Of course.  I wouldn't act any differently if you had been.''



``Really?'' I asked.



Dinah grabbed my hand.  I forced myself to shut up.



``Well.  What drugs were you taking, sweetie?''



``I don't know.''



``Can you describe what you felt when you took them?''



``Felt good.  Calm.  Relaxed.  Very sleepy, thinking through a thick soup.''



The woman was scribbling with a pen.  She shook it to banish the fly that I'd landed on the end.



``And now?  You're a little flushed.''



Was Dinah showing symptoms that I couldn't see?



``I'm hot, and my legs ache.  I'm sweating, but that might be because I'm hot.  That's all for now.  Later, I'll be throwing up, and crying.  I'll be very tired but I won't be able to sleep.''



``You've been through this before?''



``No.  Not much past this.  This will be the first time.  Hopefully the last.''



``I\ldots see.  The time of your last dose?''



``I don't know.  I couldn't see a clock.  But things start getting bad in one and a half hours,'' Dinah said.  ``They get to the very worst in one day.''



``Can you put her in a coma?'' I asked.  ``I read about it.''



``No.  I wouldn't feel confident in doing that without knowing the substances in her system.''



``Then do a blood screen first,'' I said.  ``If it's a question of money-``



``No,'' Dinah was the one who spoke.  ``Has to be the hard way.''



``Why?'' I asked.



``Because there's a seventy point one five nine percent chance that I relapse if I don't.  The cravings get too bad and I can see more cravings in the future and it gets to be too much and I go looking for some eventually,'' there was a hint of hysteria in her voice.



I sighed.  ``Okay.  No induced coma.''



``One bad week,'' Dinah said.  ``Six days.''



``Okay then,'' the doctor said.  Still chipper, strangely sounding \emph{pleased} at this situation.  ``I'll go prepare a room so you have a place to rest.  I'll grab some things to help quiet your tummy, too.''



A moment later, she was gone.



``I can stay with you,'' I said.  ``At least tonight.''



``You need to go and help the others with Noelle.''



``I will.  But first I'll see you through tonight, okay?''



She nodded.



We sat in silence for a few long moments.  The doctor stopped in to say something to Grue, and there was something about her voice, the higher pitch\ldots



``Hey, Dinah, since I can't see, can you do me a favor and tell me if you see anything around here that says `Medhall'?''



``Medhall?  No.  I don't think so.  Why?''



``These guys are too comfortable around supervillains, and this place is too expensive.  Medhall was the company that Kaiser ran, and he also ran the biggest gang of villains in town, before Leviathan came.  I'm just wondering if this was the place the white supremacists went to when they needed medical care.''



``Oh.  I don't know.''



``If it is, I'll have to have words with Tattletale.  And I guess I can see why you saw me possibly causing trouble.  If they said something to Grue, that'd probably do it.''



Dinah nodded.



I sighed.  ``A week to recuperate?''



``Six days.  Eight percent chance I need another day to rest,'' her voice seemed a touch tight, maybe a little anxious.  I wasn't sure I could blame her.



``I'm not leaving you in their care, okay?  We'll spend enough time here for me to get the details on what to do and what to look out for, and then we'll find another place to rest up.''



``Okay,'' she said, and her voice was far quieter than it had been since we'd rescued her.



It caught me off guard.  The quiet.  I'd pegged the changes in volume as being tied to her confidence, but the way she'd dropped her voice, it suggested she was anxious about something.  Something she apparently wasn't sharing with me.



``Mind if I run a few more questions by you?''



``I should save my strength, so only a couple more?''  She was still quiet as she replied.



I wasn't sure if \emph{Dinah} was aware, but the bugs I'd placed on her shoulders sensed the movement, the way she drew her shoulders in.



She was afraid?  Was it the impending withdrawal?



``Okay,'' I said.  ``Chance we come out of this okay?''



``Sixty four point two percent chance.''



``And chance the rest of the city does?''



``\ldotsNot as high.  It depends how I ask the question, but if I do-``



``No.  I get it.  If you could ballpark it?''



``Eighteen point two two five eight percent.''



``Okay.  There's going to be some catastrophic damage, then?''



``It's very likely.''



I sighed.  I still had to figure out what we were doing about Noelle.  There were roughly eight hours before we had to address that issue.  Five or six hours before we really needed to act on the knowledge, calling in help, hiring assistance or notifying the heroes.  This was a threat just one step below an Endbringer.  Hopefully Ballistic would brief us on her powers, and Tattletale could get us on target as far as her location or weak points.



Tattletale might have been the ruler of Brockton Bay in a general sense, but I was still team leader of the Undersiders.  I was blind, we had a pseudo-Endbringer to tackle, and the lives of everyone in the city potentially hinged on it.



Just had to consider my options.



``Fifty eight point five,'' Dinah said, and there was a hint of emotion in her voice.



``What?  What's that number?''



``It's my chance of getting home.''



``Why is it so low?''



She shrugged.



Did that mean she didn't know, or she wasn't willing to use her power to find out?



Then I sensed her lean slightly away from me, and I got an inkling why.



Me.



It was so seductive, when I thought about possible risk to my dad, to the people in my territory, to my teammates and friends, and even to me, to think about drawing on Dinah's assistance.  With Dinah's help, we could avoid the worst case scenarios.  And maybe in some not-quite conscious way, I was thinking about how to retain her help, one way or another.



If she was sick, after all, I could look after her while dealing with the situation.  Just a week of keeping Dinah close, drawing on her abilities to help everyone, and to ensure her safety.  With that in mind, and the way she'd clutched at me for security, I'd been assuming she'd stay with me for just a little while.



She knew that.  She saw the numbers changing.



And just with that, there was a breach in trust.  The savior wasn't quite what she'd expected?  Dangerous, even?  It explained why she was anxious.



``Dinah, listen,'' I said.  ``I can guess what you're thinking.  I don't want to be that person.  I don't want to trick myself into believing it's right or better to keep you, that it serves the greater good or whatever.  Because that's a slippery, fast road to doing what Coil was doing.''



She turned her head to look at me.



``We'll get you home as soon as possible, okay?  Within twenty-four hours.  And if there's more risk, if there's more danger to me, or to you, or \emph{everyone}?  I'll shoulder that, okay?  I'll make sure we come out of this okay.  You can go home.  You \emph{deserve} to go home.''



A full minute passed before she responded with a murmured, ``Thank you.''





