





``They won't take me back.''



``They will.''



``I \emph{saw} it,'' Dinah whispered.  ``Before I ever met Coil.  The fear in their eyes.  When I said the numbers and I was \emph{right}.  They're scared of me.  They were \emph{relieved} when I got taken.  They won't want me now that I'm free.''



``They will want you.  Just wait,'' I said.  ``They'll welcome you with open arms, and there won't even be a hint of fear.''



``I look weird.  My hair's all dry and dull, and I haven't been eating that much.  I always felt sleepy, or edgy, and was never hungry, even when my stomach was growling.  And maybe I didn't eat some because it was my only way of fighting back, the only time I could \emph{choose} something, even if it was bad for me.''



``It doesn't matter.''



``It does!''  There was a note of desperation in her voice.  ``They'll see me and I'll look \emph{different} and they'll think about all those moments when I left them feeling nervous and how there's a bunch of stuff I haven't even mentioned because it's \emph{that} bad.  I'm not even human anymore.''



``You're definitely human, Dinah.''



``Then why do they call us parahumans?  Doesn't the `para' part mean half?  Paraplegic, only half your body works.  Parahuman, half human.''



``Not exactly.  It means beside, which is how it's used with paraplegic, or paragraph.  It can also mean extra or beyond, like paranormal.  We're next to human, or more than human, depending on how you look at it.  I think it's pretty apt.  Powers, in a lot of ways, make the best and worst parts of our humanity stand out.  And \emph{that} depends on the choices we make.  Your parents can't judge you for stuff you didn't choose.''



``How\ldots how do you even \emph{know} that?''



``Which?''



``The meaning of the words.''



``My mom taught English,'' I said.  ``So I was always sort of introduced to that stuff.  And after she passed away, I maybe started paying more attention to it because it's the sort of thing she would have done.  A way of remembering her.''



``Are you an orphan?''



``My dad's alive.  I don't have as much contact with him as I should.''



``Why not?''



``It seems like every time I get closer to him, he gets hurt or put in danger.  Or I only get close \emph{because }of the hurt.  I don't know.''



``You should get back in touch with him.  Parents are important.''



``I know.''



``\emph{My} parents won't take me,'' she said.  She made a croaking noise, and I touched the bucket she was holding to ensure it was in position, held her braid so it wouldn't get in the way as she tried to empty her stomach of contents that were no longer there.



I sighed, waiting until the worst of it had abated.  When it looked like she might tip forward and fall with the puke bucket into the space between the back seat and the front seats, I caught her shoulders and leaned her back, carefully.



``How's the pain?'' I asked.



``It ends later.''



``I \emph{know} it ends.  But how is it now?''



``Hurts all over.  Painkillers didn't do anything.''



``Yeah,'' I said.  They couldn't give her anything narcotic, not with the way the doctor was suspecting that Coil had dosed Dinah with a mixture of opiates and tranquilizers to keep her artificially content and mellow.



``They're not going to take me.''



It was becoming a refrain.



``They will,'' I said.  ``I know you can't use your power right now, but they will.''



``And even if they do take me, it'll be \emph{weird}, because they can't ignore my power now.  They pretended I didn't have one.  Pretended I was an ordinary kid.  Pretended the headaches didn't mean anything, like they pretended the heart disease wasn't a thing.''



``Heart disease?  You?''



Dinah shook her head.  ``Not me.''



She didn't elaborate.  \emph{Related to her trigger event?}



``Don't worry,'' I said.  I might have gone on to try to reassure her, but I wasn't sure what to add.  I didn't know her parents.



``They'll turn me away.  I'll have to come to stay with you.  Or Tattletale.  And then it's like it was with Coil.  Not as bad.  No drugs, no being locked up.  But I'll know I can never go home.''



She was shaking, I realized.  Trembling.



``Dinah, listen.  That's the drugs talking, okay?  That's all it is.  As relaxed as they made you before, they're making you rattled now while you're in withdrawal.''



She made an incoherent noise in response.



I leaned towards the front seat.  ``Do you have a brush?''



The driver, supplied by the doctor's office, responded with only one word, ``Comb.''



``Comb will do.''



He opened the glove compartment and reached back to hand me a small comb, not even as long as my hand.



``Here,'' I said, ``Let's get you more presentable, so there's one less thing to worry about.''



I pulled off the elastic that held her messy braid together and began combing it straight.



There wasn't much time left, and still so much I should be saying, doing or asking.



\emph{Do we come out of this okay?}



\emph{We'll come out of this okay.}



\emph{Can we stay in touch?}



\emph{I'm sorry I played any part in this happening to you.}



Either I didn't have the courage or I couldn't find the right words.  Dinah wasn't in much of a state to converse, either.



I settled for tidying her hair, braiding it from scratch, and putting the elastic band in place.  Maybe it wasn't as nice as it would be without the braid, but this would be easier to manage while she was recovering.



Not even a minute later, I was holding that braid back while she hung her head over the bucket, the both of us waiting to see if she would start heaving up mere teaspoons of bile or if this latest spell of nausea would subside.  I was avoiding putting bugs on her skin, but I was aware of how she was drenched in sweat to the point that it was soaking through her clothes.  She was feverish, too.  My swarm could tell the difference in her temperature, even through her clothes and scalp.



The car pulled to a stop.



Dinah startled, as if shaken by the realization of what it meant.



``Can you go on your own?'' I asked.  ``Or maybe we could sit you down on the edge of the front lawn and beep to signal your parents?''



``Go,'' she said.



``What?''



``Go.  I'll stay in the car.  You see if\ldots''



She paused.  I wasn't sure if it was because of nausea or something else.



``If?''



``If they want me?''



I thought about arguing.  About assuring her that they would.  Then I reconsidered.  I got out of the car and crossed the front lawn to the front door of her house.



I hit the doorbell, but neither I nor my bugs could hear a sound.  No power, or it wasn't hooked up.



I gripped the heavy iron knocker and rapped on the door.



Two stray fruit flies found the parents in a bedroom on the ground floor.  They stirred, one sitting up, but they didn't approach.



I knocked again.



The dad got a cast iron pan for an improvised weapon.  It was almost comical, cartoonish.  Through my swarm, I could almost make out his words as he assured his wife,  ``\ldotsdon't know\ldots''



Whatever started or ended the sentence, I didn't catch it.



I stepped back before he cracked the door open, pan held like a weapon out of sight.



He saw me and slammed the door shut in the next instant.



I pushed the door open before he could lock it, winced at the pain that caused with my fractured rib.



He moved as if to swing at me, then dropped his arm as he reconsidered in the face of the thick cloud of bugs that stirred around me.  I wasn't sure how much he could see.  There weren't any streetlights, or lights on inside, but I would be backlit by moonlight.



``I'm not here to cause trouble, Mr. Alcott,'' I said.  ``And I don't mean to scare you.''



``What do you want?''



``I brought Dinah.''



He froze.



``If that's alright,'' I said.



Not turning away from me, he shouted, ``Anna!''



His wife exited the bedroom to stand in the doorway, peering out into the hallway.  She reacted as she saw me.



``Extortion?'' he asked.  ``We don't have anything.  You can take anything we have here, but it's not much.''



``Not extortion.  The man who took her died.  I'm bringing her back.''



``Please,'' the mom said.  ``Where is she?''



``Before I go get her,'' I said, ``You should know.  There's no sign he touched her.  He didn't hurt her, not physically.  He did everything he could to take care of her, in a utilitarian sense, but she was still a prisoner.''



Without working eyes, I couldn't see their expressions.  Horror?  Grim acceptance?



``She was drugged, often and heavily.  She's in the middle of recovery, and it isn't pretty.  No narcotics, no painkillers, and no tranquilizers, maybe for the rest of her life.''



The mom made a subvocal noise.



``She's an addict?'' the dad asked.



``Yes.  And she's a touch malnourished, and above all she's scared.  I wouldn't have brought her yet, but I thought it was more important that I get her away from anyone who would do what Coil did, using her for her power.  I wanted to get her home.''



``She has abilities, then?'' the dad asked.



\emph{Why else would Coil take her and keep her?}



``\emph{An} ability, to be specific,'' I said.  ``Does it really matter?''



The dad shook his head.



``I'll go get her, then.''



I walked out to the car and opened the door next to Dinah.



``They don't want me.  They won't.''



``Come on,'' I said.  I extended my hand.



``Maybe we should wait until I'm not sick anymore.  If they see me like this, they might have second thoughts.''



``They won't.  And we agreed you should go home sooner than later.  Come on.''



She put her hand in mine, and I could feel it shaking in the half second before I got a firm grip.  I supported her as she got out of the car, then walked her back toward the house.



Mrs. Alcott made a noise somewhere between a moan and a cry as we approached the front door.  I moved my bugs out of the way and let go of Dinah the second her mother embraced her, right in the middle of the front lawn.  The father was only a step behind, dropping to his knees to wrap his arms around them.  A family reunited.



It was a rare thing, I was finding, that a family was both intact and functioning.  Too many of the people I'd interacted with so far were separated from the families they \emph{should} have by death, by pain, misunderstandings or abuse.



I turned to leave.



``Thank you,'' the dad called out.



I almost stopped.  Then I kept walking towards the car.



``Don't thank me,'' I said, without looking back.  I wasn't sure if I was loud enough for him to catch it.



It didn't feel \emph{good}, but it didn't feel bad, either.  I'd played a part in her being taken from her family.  Maybe a small part, but a part.  I'd done something to make up for that.  The real sacrifice, the \emph{real} atonement, would be dealing with what came next.  Dealing with Noelle and the end of the world without using or abusing Dinah's powers.



I wasn't sure I felt good about that.  I'd gotten this far by making the most out of every resource I had available, and by being \emph{smart} about things.  This was throwing away a resource, tying my own hands.  The decision felt \emph{dumb}, even as I knew it was the right thing to do.



I climbed into the car.  Settling into the middle of the back seat, I swept my bugs over the area as a matter of habit.



Two folded pieces of paper were stuck in the flap behind the driver's seat, where they hadn't been before.  I picked them up, tried to view them with both my regular eyes and my bugs, then settled for tucking them into my belt.



Had to get someone to read them for me later.



``Where to?'' the driver asked.



``Downtown.  I'll tell you where to stop.''



\sectionbreak



The others were gathered outside Tattletale's new headquarters.  The Undersiders were all there, Bastard and Bentley included.  Ballistic was present as well, though I hesitated to call him a member of the group.



There was also someone who I hadn't expected.  Parian.  My recruit, after a fashion, the doll girl was dressed in a crisp new frock, accompanied by a giant stuffed penguin fashioned from cloth.



``You're late,'' Ballistic said.



``Had an errand to run.''



``Sent the girl home?'' Tattletale asked.



``Yeah.''



``Good,'' she said.  ``Feel better?''



``Some,'' I replied.  I turned to Parian.  ``Didn't expect to see you here.''



``Tattletale got in touch.  I\ldots I apparently missed a lot.''



``You're up for this?''



``No.  But I want to know what's going on, in case it affects my territory.''



``She's taking over my shelter and the surrounding area,'' Tattletale said.



``Makes sense,'' I said.



``Glad everything's getting sorted out,'' Grue said, ``But we've got an hour and forty minutes until dawn, and we \emph{really} need to deal with the present situation.''



Tattletale said, ``Let's talk as we walk, then.  We have one sighting of Noelle.  She left ten minutes ago, and I doubt we'll run into her, but we could get info, something that'll let us track her, or we'll at least be in the right general area.  Sorry, Skitter.  We found Atlas, but he's stashed halfway across the city.  So transportation might be a little awkward.''



I only nodded.



Parian took the penguin apart and created a longer, broader form: a dachshund, in black and white.



``This is so lame,'' Imp said.  ``How are you supposed to build a decent rep if you're caught riding a wiener dog?''



``It's the only thing long enough,'' Parian said.



``Snake?''



``Too much wear.''



``If you don't like it,'' Grue said. ``You can walk.  It's functional.''



``You've fallen so far, man,'' Regent murmured, wry,  ``You used to \emph{care} about these things.''



``Because they kept us alive, kept our enemies off our backs.  I don't care too much about anyone dumb enough to ignore the fact that we \emph{own} this city but care about how we travel.''



``I could ride Bentley,'' Imp suggested.



Regent commented, ``You're calling him by his real name, now?  Didn't you call him slobberjaws, just a little while ago?''



Rachel was looking at Imp.  Glaring?  ``You're not riding him.''



``You \emph{really} care?'' Imp asked.



``Not about the name,'' Rachel said.  ``About respect.''



Imp groaned audibly, and Regent laughed.



My bugs helped me catch the muttered exchange between the pair.



``Why?''  Imp asked, in her most wounded voice.



``Payback.'' Regent replied.



Rachel was looking at me, the offer unspoken.



I accepted it, reaching up to take Rachel's hand and using her help to climb onto Bentley's back, settling in behind her.



We walked briskly alongside the cloth dachshund that bore the burden of the rest of the group; Grue, Tattletale, Regent, Parian and Ballistic.



``Everyone's kosher with me taking the seat of power?''  Tattletale asked. ``This isn't me being manipulative like Coil, but I do consider us partners, I want us working side by side, even if our roles are different.''



``Partner?  You're in charge, aren't you?'' Ballistic asked.



``I'm\ldots headquarters.  Ops.  Management.  Skitter's our real leader, our field commander.  If it comes down to it, she can call the shots.  I'll back her up.''



``If she's up for it,'' Grue said.  ``She's blind, and neglected to mention it before the events earlier tonight.''



``It doesn't matter that much.  I don't need my eyes when I can use my power,'' I said.



``I'll have to take your word for it.''



``What are we up against?'' I asked, aiming to change the subject.  ``Ballistic, can you fill us in?''



``It's why I'm here.  Consider Noelle a triple threat,'' he said.  ``She's strong, she's got nothing to hold her back, now, and she's \emph{smart}.''



``She was your team leader, right?'' I asked.



``She was the leader before all of this started, yeah.  You have to understand, she's a natural \emph{tactician, }and tacticians come in two varieties.  There's the strategists that think things through, innovate, and analyze.  Then there's ones that go by instinct.  Noelle's the latter.  Not to say she isn't good if given a chance to plan, but she can get a sense of the current dynamic on an intuitive level, play things by ear while making spur of the moment calls.  Those calls turn out to be the right ones, not because she's lucky, but because she grasps the situation so quickly that it \emph{looks }like she didn't give it any thought at all.''



``She's quick witted, then,'' I said.



``Not exactly what I meant.  Might be that I'm extrapolating too much from too small a sample of info.  Far as I know, she's never been in a serious fight, but when you add that to the whole \emph{strong} and \emph{desperate} bits I just mentioned, it makes for a scary combo.''



``How's that?'' Grue asked.



``Right now, she's scared, angry, desperate and frustrated, except all the dials are turned up to eleven,'' Ballistic said.  ``She can't hold back her emotions like she used to.  She goes berserk at the drop of a hat, and this?  Losing what she sees as her last shot?  That's more than a dropped hat.  If she were a person who relied on her brain in a crisis, she'd be at a disadvantage, because she's not in any position to think straight.  The way she \emph{really} operates, though?  She won't be any less effective because of that fear and panic.  I don't plan on getting in her way.  I'm sitting out on this fight, for the record.''



``You're out?  You're not working with us?'' Grue asked.



``I'm holding territory, but I'm not a member of the team.''



``Same,'' Parian said, ``Sorry.''



``You don't have to be sorry,'' I said.  ``But I think you're underestimating how bad this situation could be.  I don't think we can afford to have anyone sit out.''



``She's scary,'' Ballistic said.  ``Let's settle for that.  You don't get within Behemoth's range, you don't aim for the long fight against Leviathan, and you don't send everyone against the Simurgh at once, or you're screwing yourself over.  Trust me when I say this is better all around if I skip this fight.  She knows me, and she'll use me against you.''



``You talk about her being clever, but she didn't seem that on the ball when we talked to her over the phone, back in your base,''  I said.  ``You guys were lying to her about Tattletale, about Dinah, and other stuff.  If she's that clever, why didn't she pick up on it?''



Ballistic sighed.  ``Honestly?  She put her trust in Krouse, in Trickster.  He betrayed that trust, and he did it pretty damn well.  I don't fault him for it, exactly.  She couldn't know the whole truth, or we'd be in \emph{exactly} this situation, just at a worse time.''



``But you do fault him for something,'' Tattletale said.



``He became team leader more because he's fast at thinking on his feet than because he's good at making the right call.  He took it on himself to make a whole lot of wrong calls.  I let a lot of that slide because he used to be a friend.  And maybe because they weren't blatantly wrong.  Just a little wrong, a little disagreeable.  But at some point every call was a disagreeable call and every word out of his mouth became a white lie.  He started lying to \emph{us} for what he saw as our own good.  Not Noelle with her delicate state, but \emph{us}.''



``And you realized he was never going to change,'' Tattletale said.  ``His focus would always be on Noelle and himself, no matter what happened.''



``Yeah.  We shouldn't discount Trickster, by the way.  Either as a threat or as a possible solution.''



``I hadn't forgotten the possibility that he'd stick around and make life harder on us,'' Grue said, ``But \emph{solution}?''



``Yeah.  Whatever else, I'd say Noelle still believes in him.  We can use that.  If we're willing.''



``And that's only \emph{if} we can get him on board,'' I said.



Ballistic nodded.



``What does she do?'' Grue asked.



Ballistic sighed.  ``Besides the ridiculous super strength, durability and the regeneration?''



``Besides that,'' Grue said.



``To put it briefly, if it's dead, she absorbs it and it becomes a part of her-``



``Powers included?'' I asked.



``Don't know.  Haven't had cause to believe it.  In terms of raw material, raw mass?  Yeah.  She eats, she grows.  But here's the thing.  If she absorbs something \emph{alive}, she clones it.  More clones if she's angrier, we think.  We don't have a large sample size of incidents.''



``Clones?'' I asked.  ``Isn't that an advantage for us?''



``No.  Because whatever they are, the extras come out \emph{wrong}.  They come out ugly, their powers don't always work exactly the same way, they're screwed up in the head, but all that aside, they're stronger, tougher, they have the memories of the parent.  Sometimes that means they're just homicidal.  Other times, it means they're just as sane as you are, but their priorities are reversed.  They want to end your existence, kill everything you want to protect, hurt everyone you care about, and dismantle your life.''



``Evil twins,'' Regent said.  ``She makes evil twins.''



Ballistic nodded.  ``And that's why I'm sitting this one out.  She'll come after me if she sees me, especially if she heard the bit about my defection.  If she gets me, that's even worse, because the clones she'll get are capable of killing anyone and everyone here, easy.''



Bitch spoke for the first time.  ``Animals too?''



``Animals too.  And microbes too, based on stuff she's said before, though she might just treat them like she does dead material.  I don't know.  For all we know, it ties into some other power.''



``Do the clones have an expiry date?''  I asked.



``Not as far as I know.  Any time we've had to deal with them, we were pretty ruthless in putting them down.  They sort of made a point of being too problematic to be left alone.''



``They're still \emph{people},'' Parian said.



``No,'' Ballistic replied.  ``They really aren't. Trust me on that count.''



``I've got soldiers at key locations, keeping an eye out,'' Tattletale said.  ``Just a few guys, and I'm paying them an astronomical amount.  I won't be able to keep it up for more than a few days.''



``Which is how you got this lead?'' I asked.



She nodded.



``Okay,'' I said, ``Good.  But we'll need a way to deal with her.  Ballistic, you said she regenerates?''



``Not that fast, but fast enough.  Her lower body is tougher, but her upper body isn't exactly vulnerable.  I've seen her take bullets and barely even flinch, and that included one to the head.  They do damage, maybe, but it heals too quickly for it to matter.  And I think she's gotten bigger and tougher since I saw her last.''



``When was that?''



``Maybe a week after we got to this city.  A while before Coil put in the first vault door, there was just a garage door.  I didn't want to risk getting too close, not with the lethality of my power and the damage she could do.  Her appetite's increased, so it might be a pretty dramatic difference in strength from the last time I saw her out and about.  You guys are going to have your hands full trying to kill her.''



``I don't want to kill her,'' I said.  ``Not unless we absolutely have no other choice.''



Ballistic turned my way, and he had a funny tone in his voice as he asked, ``How do you \emph{think }you're going to handle this?''



``Containment,'' I said.  ``If I get enough spiders together, I could try to surround her in web.''



``Not going to work,'' Ballistic said.



``It almost worked against Crawler.''



``She's stronger than Crawler.''



``Then we go to the heroes.  We get their assistance,'' I said.  ``Containment foam on top of my web.  Vista to slow Noelle down, Clockblocker to put her on pause.''



``Tattletale told you, didn't she?  That we think she's turning into an Endbringer.  Why is lethal force okay against Leviathan but not against Noelle?''



``She's still a person, under it all,'' I said.  ``She deserves a chance.''



``You don't seem to care at all about the subject of killing a \emph{friend}, Ballistic,'' Tattletale added.



``She's not my friend.  She's not the person I knew.  Maybe she has the same memories, fragments of the same personality, but that's only surface stuff.  Because even the bits that \emph{look} like Noelle aren't really anything resembling the original.  She wouldn't be able to heal bullet wounds like she did if they were.  Stands to reason the bits that \emph{think} like her aren't either.''



``Pretty cold,'' Tattletale said.



``Fuck you,'' Ballistic replied.  He slid off the stuffed animal's back.  ``I hope what I said was useful, and I wish you luck, but fuck you.  You don't get it.''



Parian's animal had stopped, but Ballistic was already striding away, in the general direction of his lair.



``Go on,'' Tattletale urged Parian.  The stuffed dog started walking again.



``You told me I could protect people,'' Parian said.  It took me a second to realize she was addressing me.  ``How do I do that?''



``We could use your stuffed animals.  If she can't absorb them, then they're frontline combatants we can use.''



``I don't want to fight.''



``I \emph{really} don't think we have a choice.  You fought Leviathan,'' I said.



Parian shook her head, ``I almost wish I didn't.  I only did it because I promised myself when I was a kid, when I first learned about the Endbringers, that I would fight them if I ever got powers.  That's why I did it, because I didn't want to betray the kid version of myself.''



``Wouldn't your child-self want you to do this?''  I asked.



``I don't know.  But I didn't make any promises to myself about this.''



Tattletale cut in.  ``Heads up.  I don't think we're the only ones checking out the scene.''



``Who?'' Parian asked.



``The Protectorate.  The Wards.  If you're not up for a potential fight, this is the time to back off.''



``The Wards?'' Parian asked.



Tattletale nodded.



``I'll stay.  I won't fight, but I'll stay.  I made my decision and I'll own up to it.''



\emph{It's at least one more body on our side, giving them less reason to pick a fight}.



``We do this peacefully,'' I said.  ``We need their help, so we avoid confrontation.''



``This isn't going to work,'' Regent said.  ``Just saying.''



``We'll try it anyways,'' I replied.



I could sense the heroes well before we reached them, gathered by a ruined building.  I used my bugs to get their attention before we appeared around the corner.



``Undersiders,'' Miss Militia spoke, rifle raised and pointed in our direction.  The other members of the local hero teams were at the ready just behind her.  I noted Flechette gesturing, Parian shaking her head.



``Miss Militia,'' I responded, when I realized none of the others were responding.  \emph{Should have hashed this out with Tattletale.  She can do the negotiating with hostile parties better than I can.}



``You do this?''  She jerked her head in the direction of the wreckage, not moving the rifle.  Her voice was hard.



``Indirectly,'' I replied.  ``But not really, no.  I don't know what that \emph{is}, exactly.''



``I find that hard to believe,'' she responded.  ``A hell of a lot of damage, reports of howling eerily similar to the reports we've had for Hellhound's animals, and let's not forget your penchant for kidnapping the good guys.  Shadow Stalker, Piggot, Calvert\ldots''



\emph{Kidnapping heroes?}



With my bugs, I did a head count.  Someone was missing.



\emph{How?  Dinah said Noelle wouldn't do any major damage before dawn}.



``Vista,'' I finished Miss Militia's thought.  ``You're talking about Vista.''





