





Miss Militia didn't respond.  She stared down the length of her gun at Tattletale.  I could believe that if we gave her cause, any of the rest of us were an instant away from getting shot.  We had bulletproof armor, but there wasn't anything saying she wasn't using the fanciest armor-piercing rounds.  Her power supplied whatever hardware she wanted.



``We didn't take Vista,'' I told her.



``It doesn't make sense,'' Tattletale said, ``We'd take her, do that sort of damage, and then come back?  Approach you guys peacefully?''



``I'm beginning to see why Armsmaster was so frustrated with you, Undersiders.  Every time we run into you, we're left in the dark, vast amounts of information missing from the overall picture.  There's always surprises.  So I'm paying very close attention to what you are saying.  Case in point, you say Vista was \emph{taken}, and not murdered.''



``I don't think she was killed,'' I said.  Tattletale nodded.



``That's good to know,'' Miss Militia said.  She sighed, ``When you're going on the offensive, there's nothing held back, you don't pull any punches, short of murder\ldots and you apparently came \emph{damn} close with Triumph, Skitter.''



Triumph folded his arms.



She continued, ``If you're not trying to kill us, you're approaching us with open arms, asking for help, putting us in a situation where we \emph{can't} accept without breaking our rules, but refusal comes at a cost.''



``It's that second bit,'' Imp said.  Some of the heroes wheeled around to find her standing on the opposite side of her group.  I managed to hide my own surprise.  Imp added, ``We're here because we need help.  This is a nasty one, too.''



Miss Militia turned back to me, and her voice was a little harder.  ``I thought so.  It's your pattern.  Except there's always information missing.  Information withheld.  You said you were \emph{indirectly} responsible for this?''



``You caught that,'' Tattletale said.  She looked at me.  ``Should we dish out the dirt?''



``Yeah,'' I said.  ``Have to anyways.''



``Full disclosure,'' Tattletale said.  ``We were working for Coil.  The Travelers were too.''



Miss Militia didn't move a centimeter.  Some of the other heroes did.



``He's dead, in case you weren't aware,'' Tattletale said.  ``And the Travelers are a little upset, because they were counting on him to help them out.''



I could imagine Tattletale smiling.  \emph{She's misdirecting them.  They think he died at the debate, but she's talking about the real death}.  \emph{The death at my hands.}



Miss Militia shook her head.  ``I doubt this was the Travelers.  We heard howling, and this wasn't Genesis.  Analysis of her file by some of our top guys suggests she has limits to the strength of whatever forms she's chosen.  Strong, yes, but not enough to tear half the wall off the front of a building in the time the witnesses described.  I would, however, believe Hellhound's dogs could do it.  Besides, Genesis has never been on record shapeshifting to resemble someone or \emph{something}.''



\emph{Never?} I thought.  She crafted her bodies in a dream state.  I knew she'd made a body that resembled her real self, but the rest\ldots  Did it take too much effort to get the aesthetic details exactly right, to the point that it cost her in other departments?



``When the Slaughterhouse Nine attacked,'' I said, ``Do you remember who they targeted?''



``Armsmaster, Regent, Hookwolf, Panacea.  Two more.  With the appearances Mannequin and Burnscar made in the Boardwalk, we belatedly discovered Hellhound was another, and we were theorizing you were the last of them, Skitter.''



``I got in their way too many times,'' I said.  ``But they didn't want me.  But the last one was Noelle.''



Her gun shifted a fraction towards me.  I wasn't sure she was aware she was doing it. ``Noelle?''



Tattletale spoke up, ``The Travelers have two other members who don't see much action.  Oliver handles their day-to-day stuff.  Finds and prepares places for them to settle down, gets food, looks after Noelle.  Noelle\ldots''



``New York,'' Miss Militia interrupted.  ``She's the one that's responsible for the disappearance of those forty people?''



``I wouldn't be surprised,'' Tattletale said.



``The reason the Travelers have been operating like they are,'' I told Miss Militia, ``Going for the quick and easy cash grabs and constantly moving, it's been for her sake.  Trying to find someone who can help.  They found Coil, or Coil found them, and they thought they had the answer they needed.  Except now Coil's dead.  Noelle's snapped, and it's very possible Vista was her first captive.''



``What does she--'' Triumph started.  He stopped as Miss Militia raised one hand.



``You're good at this, Undersiders,'' she said.  ``But I do learn my lesson.  I won't get caught up in your story, I know you'll \emph{have} to give me the details, if this situation is as serious as you say.  But let's postpone that for a minute.  Why don't you start off by explaining how you're indirectly responsible for this.''



I turned to Tattletale.  She gave her head a small shake.



``What aren't you telling us?''  Miss Militia asked.



``Stuff,'' Tattletale said.  ``Surrounding the circumstances of Coil's death.  But getting into the particulars would create more problems than it solves, for you guys and for us.''



``I dunno,'' Assault said, from behind Miss Militia, ``I doubt staying quiet is going to help you much.''



``Did you have something to do with the explosion at the town hall?''  Miss Militia asked, and there was a note of anger in her voice, ``The way things went wrong?  The deaths of those reporters, the injuries sustained by the retired Director and the candidates?''



``No,'' I said.  ``I swear on everything I stand for that I, \emph{we}, didn't play any part in planning or setting that in motion.''



``You can understand if we don't take you at face value on that, nice as it sounds,'' Assault said.



``If it helps,'' Tattletale said, ``Get your hands on the evidence from the scene, some of the blood and bits from the bodies.  Send them out of town.  \emph{Discreetly}.  Get another lab to run DNA tests.''



``Why?''



Tattletale shrugged.  ``It's pig meat.  Almost all of it.  Glued together with transglutaminase.  Human bone, and human blood, probably, but if you look for it, you'll find antifreeze.''



``Antifreeze?''



``Glycerol.  It's how they store it at blood banks.''



``You're saying it was staged,'' Miss Militia said.  ``Despite the fact that we had Wards on scene, innumerable witnesses.''



``Despite that.''



Miss Militia straightened a fraction, ``And of course, we can't check it \emph{now.  }So you're expecting us to work with you in the meantime, help you with whatever problem you're suggesting you're partially to blame for setting in motion, and when the lab tests come in, long after the situation's resolved, we'll find you were lying.''



Assault added, ``And somehow, \emph{conveniently}, you come out ahead when all's said and done.  A handful more of your enemies injured or \emph{dead}.''  There was a hint of emotion punctuating the end of the statement.  \emph{Battery}.



``Telling the truth,'' Tattletale said.



``This situation's serious,'' I told Miss Militia, ``And if you do what we're suggesting, I can assure you, we don't wind up in a better position at the end of this.''



``Why's that?'' Miss Militia asked.



It was Grue who answered her, breaking his silence with his deep, eerie voice, ``Because we're recommending you call in the big guns.  Call in everyone.''



``Class S threat,'' Tattletale said.  ``Or damn near.''



The tip of Miss Militia's gun wavered as she started to react and then stopped herself.  Neither she nor any of the heroes moved or spoke for long seconds.



When she did speak, she said, ``There's six class S threats active in the world at large.  The Endbringers make up three of them.  The Slaughterhouse Nine as a group are a fourth.  You're saying this Noelle is on par with one of them?''



``She's a nascent Endbringer,'' I said.



``Bullshit!''  Triumph shouted, not a half second after I'd said it.



``Fuck me,'' one of the Wards said.  It was only after he opened his mouth again that I saw it was Weld.  ``Please tell me this is another one of Tattletale's mind-games.''



``Explain.'' Miss Militia demanded.



``She's \emph{maybe} a nascent Endbringer,'' Tattletale said.  ``It's one theory.  Her powers are transforming her, and she's getting less human, getting tougher and more desperate every day.  Coil was keeping her contained, with heavy vault doors and promises of a fix.  Now she's free and she's \emph{pissed}.''



``And this hypothetical individual has Vista?'' Clockblocker asked.



``It's very likely she has Vista,'' Tattletale confirmed.  ``Coil's precog said she wouldn't cause any \emph{real} damage until dawn.  That's\ldots one hour and twenty-nine minutes from now.  I guess this kind of incident doesn't count as anything serious.''



``You have Coil's precog in your custody?''  Miss Militia asked.  ``Dinah Alcott?''



``I took her home,'' I said.  ``Her powers are currently disabled, so resist the urge to go to her and ask her for help with this situation.  Everything she's been through, she deserves some peace.''



``Assault,'' Miss Militia said, ``Let's get some confirmation that at least \emph{some} of what they said is the truth.  Get in touch with the Alcotts.''



``On it,'' he said.  He drew a rugged smart phone from his belt and put it to his ear.



``I think it's time you guys offer the particulars on this `Endbringer','' Miss Militia said.



``She's as strong as Leviathan, physically,'' Tattletale said, ``She's not as tough, based on what I've seen.  Have you read the notes on what I told Alexandria after Leviathan's attack?  About the density of Leviathan's body?''



Miss Militia nodded.  ``Higher density as you penetrate deeper to the core, to the point that it bends the rules of how molecules and atoms should work.  It makes sense.  Armsmaster had a molecule-severing weapon that couldn't cut through all of Leviathan's hand, and it explains why nearly all the damage we do is so superficial.''



``Noelle doesn't have that yet.  I'm not sure if she ever will.  We don't know if she's \emph{really} becoming an Endbringer or not.  What I've seen of her was only partial, a camera feed with dim lighting on the other end,'' Tattletale said.  ``But everything she eats gets added to her biomass, and I think she'll probably reach a critical point and stop growing, start fortifying what's already there instead.''



``She's big?''  Weld asked.



``She's big,'' Tattletale said.  ``And if she gets her hands on you, she'll eat you whole.  Spit you out along with a copy.  Copies with powers like yours.  Stronger, tougher, meaner.  Understand?  When this fight starts, it starts for real.''



``She duplicates people,'' Miss Militia stated.



``And the duplicates\emph{ aren't} on our side,'' Tattletale replied.  ``You're going to have to call for backup at some point, it's just a question of whether you do it \emph{before} shit goes down or \emph{after}.  When you do get in touch with the PRT heads and get the a-ok to call a red alert or whatever it is you do, you're going to want to be \emph{very} careful about the kind of cape you request, because we might wind up fighting them.''



Assault had finished his phone call and was waiting for Tattletale to finish talking.  Miss Militia turned her attention to him, and he said, ``Story checks out.  Kid's at the hospital, recovering from a long stint of drug abuse.''



``The situation they're describing is too dangerous to be ignored.  We'll move forward with this.  Tentative cooperation,'' Miss Militia announced.  ``In exchange for our trust and our assistance, the Undersiders will give us one hostage.''



``How about me?'' Imp offered.  Her tone was light, joking.



``Someone who we can keep track of,'' Miss Militia said.  ``Rachel Lindt.  Hellhound.  If you'd please step into the van?''



``Fuck that,'' Rachel replied.



``That's a disaster waiting to happen,'' Grue said.  I couldn't help but nod in agreement.



``You, along with Skitter, are problematic due to the sheer amount of damage you could do in the enclosed space of a van.  Tattletale's more damaging in other ways.  It would help if we knew exactly what her powers were\ldots''  Miss Militia trailed off, inviting a response.



``Not sharing,'' Tattletale said.  ``And I just had my turn at being a hostage.  Not sharing the details on \emph{that} either, for the record.''



``Regent's too dangerous.  We don't know exactly how long it takes for him to achieve full control, and our records suggest he can \emph{regain} control instantly.  Even if we assume it takes an hour or more, we can't trust that we won't end up in a crisis situation where Regent's being kept in custody for an extended period and gets the opportunity to use his power on someone.  Not to mention the possibility that he could call Shatterbird to his location.  Separated from her dogs, Rachel Lindt is the least threatening and most vulnerable member of your team.  The optimal hostage, if you will.''



``And she won't accept being separated from her dogs or being kept in custody,'' I said.  ``I will.  I can hand you my weapons and send my bugs away.''



``Skitter,'' Grue said, ``No.''



Miss Militia folded her arms, unconvinced.



I reached over my shoulder, slowly, and unbuckled my utility compartment.  Tattletale grabbed it for me as it came free, and the straps fed out through the rings beneath the shoulder panels.  She handed it to me, and I drove away the bugs I'd gathered inside.  When they were gone, I sent away the bugs that were nestled in the midst of my hair, beneath each of my other armor panels and the `skirt' of my armor, where it covered the scorched leggings of my costume.



``So many fucking bugs,'' Clockblocker said.  ``They have to weigh as much as she does.''



``No, not as much as you'd think,'' I said.  I turned to Miss Militia.  ``Satisfied?''



She extended a hand for the concave, spade-shaped piece of armor, her gun turning into a handgun in the meantime.  ``Triumph, pat her down.  Everyone else, get ready to mobilize. Assault, you'll be riding my bike.  I'll sit in the van.  Weld, Clockblocker, Flechette, and Kid Win, with me.''



I waited while Triumph roughly pat me down, running his fingers into the folds and crevices of my armor and beneath my belt.  He found the two pieces of paper I'd folded and tucked inside, shook them out as if there might be powder inside, unfolded them, read them, then put them back the way I'd had them.



I felt like saying something to him, but wasn't sure what.  \emph{Sorry for attacking your family and nearly murdering you?  }It sounded almost taunting.



Miss Militia led the way to a containment van, and I followed, feeling oddly lightweight.  She opened the back, indicating we should gather inside.



They arranged themselves with Clockblocker and Weld sat to either side of me, Miss Militia, Flechette and Kid Win opposite me.  The door slammed shut as Kid Win got himself seated.



I had only a few bugs in place to get a sense of their positions.  Few enough that I might have lost track of who was who if I wasn't careful.  Using one of these bugs, I did a minor, peripheral sweep.  They didn't have weapons pointed my way, but Flechette and Kid Win did have weapons on their laps, a crossbow and laser blaster.



``You're shorter, looking at you like this,'' Clockblocker said.  ``Tall for a girl, but\ldots not \emph{tall}.''



``Sorry,'' I said.



``You didn't get rid of all your bugs,'' Clockblocker commented, as the truck started moving.  He was looking in the direction of the patrolling mosquitoes and no-see-ums.



\emph{He noticed}.



``Not all,'' I agreed.



``Why not?''



\emph{Because I'm blind, and I'm utterly helpless if you take all the bugs away}, I thought.



``Too much of it's automatic,'' I said.  ``I got in the habit of using my power to survey the situation, and now it happens even without my thinking about it.''



``Thinker one,'' Weld said.  ``Because your bugs let you sense things to the point that you might be a short-range clairvoyant.''



``That's about what the Director said,'' I replied.



I heard a click, and bugs moved to the source of the noise to investigate.  Miss Militia had my utility compartment in her lap, and she was holding a handgun.  Mine.



``Only one shot remaining.  Two reasons that might be the case,'' she said.  ``Saving it for yourself, or it was used and you haven't reloaded.''



``The latter,'' I replied.



``Who have you been shooting?''



\emph{Your Director}.  ``Mannequin.  And shot through some boards so I could break them.''



``Oh?''



``Long story.  I haven't really thought to reload it.  I don't use the gun much.''



``Obviously,'' she said, but she didn't elaborate.  ``String?''



``Can you leave stuff where it is?''  I asked.



``I'm curious why you have coiled string in your backpack here,'' she said.



``It's a utility compartment, not a backpack.  It's so I don't have to have the spiders make it in the middle of a fight.''



``Spider silk,'' Kid Win spoke his realization aloud.



Miss Militia continued, ``Pepper spray.  Changepurse with\ldots cotton swabs?  I see, it's to mask the rattle of spare change.  And smelling salts, needles.''



``Please leave everything where it was,'' I said, a little firmer.



I'd collected a few bugs on the various objects she'd withdrawn from the interior of the compartment.  I sensed her putting things back, watched to make sure she was putting everything back properly and in the right place.



Clockblocker, though, leaned across the back of the van and picked up the baton.



``You've got stuff like this that's high quality, but then the other stuff's so mundane,'' Clockblocker commented.  ``Odd for someone half the nation's paying attention to.''



``I wouldn't know,'' I said.  ``Not really watching TV these days.''



``You guys took over the city, which is something that's usually limited to psychos like Nilbog or the third world nations.  I guess with Coil gone, you're queen of the local underworld.  Or is it Tattletale who's taken that position?''



``We're partners.''



``You sound so matter of fact about it,'' Clockblocker said.  ``You're not ashamed?  Guilty?  Or proud?''



``Stand down, Clockblocker.  She was gracious enough to be our guest.  Don't provoke her,'' Miss Militia ordered.



``I'm not bothered,'' I said.  \emph{I'm more annoyed at you picking through my equipment}.  ``And I don't feel anything about being in charge.  It is what it is.''



``And you're not afraid at all, being a hostage?'' he asked.



``Should I be?''



``You violated the code by association when you took someone, took \emph{control} of someone.  The same someone who you saw unmasked.  You violated the code again when you attacked Triumph's family.  So what's stopping us from tearing off your mask right now?  The same code you've disrespected and broken?''



``Look me in the eye,'' I told Clockblocker, turning my head to face him, ``And tell me you don't think Shadow Stalker was a deeply damaged, \emph{broken} person before we ever got our hands on her.''



He faced me square on, ``She was also a hero.''



``She was a hero because the other choice was juvie,'' I said.  ``In the months leading up to our kidnapping her, she was using real crossbow bolts.  Shooting them at people, Grue included.  If I remember right, she wasn't supposed to have or be using any lethal ammo, on penalty of jail time.''



``Do you have evidence?'' Miss Militia asked.



``Would it matter?  \emph{Does} it matter?  Judging by what I saw, in my limited interaction with her, she was pretty psychotic.  There's no way you guys spent all that time with her without something crossing your radar.  The night we took her, I baited her out and she tried to \emph{cut my throat.''}



``I understand where you're coming from,'' Miss Militia said, ``But again, I have to ask for evidence.  I can't take you at your word, there's procedures to be followed.''



``Procedures that tie your hands,'' I said.



``And they protect us at the same time.''



``If you're looking for a reason why we're in charge,'' I said, turning towards Clockblocker, ``That'd be a good place to start.  You guys \emph{knew} you had someone bloodthirsty and fucked up working beside you.  You accepted it, probably accommodated her.  Probably cut her slack in other areas, because I doubt she was an angel outside of costume, either.''



I let that sit with them for a moment.



``Yeah,'' I said.  I shifted positions on the bench.  ``We aren't limited by oversight and bureaucracy, and we don't pretend our lunatics are kid-friendly.''



``And without that oversight, you're free to kidnap people like her and subject her to torture,''  Clockblocker said.



``That's enough,'' Miss Militia said.  She wasn't quite as sharp as before, but her words were somehow more effective.



We rode on in silence for a few long moments.



``You smell like smoke,'' Clockblocker said.



``Clockblocker,'' Miss Militia said, ``I reserve every right to \emph{adjust} your patrol schedule if you won't stop \emph{engaging} Skitter.''



``I'm \emph{really} okay,'' I told her, keeping calm.  \emph{If I'm ever going to shake the idea of Skitter being this unpredictable, dangerous felon, it's now.  }``I'm not going to flip out and hurt someone because I don't like what they're saying.  When I said I shot some boards, it was to escape a burning building.''



``Coil wasn't lying when he said he set your headquarters on fire,'' Weld commented.



``He was,'' I replied.  ``This was something different.''



``Fuck it, give me shit patrols,'' Clockblocker said.  ``I'm not going to just sit by and obey orders, when I have a chance to get answers.''



``Clockblocker,'' Miss Militia said the name in a warning tone.



``That's the kind of attitude I'm talking about,'' I muttered.  ``Recognizing when the bureaucracy is hindering more than helping, pushing against it.  I can respect that.''



``Don't compare me to you,'' Clockblocker said.



``Okay,'' I said, smiling a little behind my mask, ``I won't.''



``I'm wondering how the fuck you can justify doing any of the shit you've pulled and act high and mighty.''



``I won't deny I've done stuff,'' I said, ``But I somehow doubt it's the same stuff you're thinking about.  But I had reasons for everything I did.  If you want to \emph{tell} me what you think I've done, I can try my hand at explaining myself.  \emph{Provided} you're willing to hear me out.''



``Clockblocker,'' Kid Win said, ``Listen to Miss Militia.  This is the kind of stuff that goes on your record.''



Clockblocker shook his head.  ``Fuck my record.  Let's start with the takeover.  Justify that.''



``It put me in a position to help people.  Visit my territory.  People there are healthier, happier, safer, because of what I've done.''



``Except the ones Mannequin and Burnscar killed.''



I didn't have a ready reply to that.



``No comment?''



``I tried,'' I said.  ``I did what I could to help the people in my territory.  Maybe my being there did more harm than good.  I don't know.  But I tried to help.''



``Let's call that one a draw, then.  What about how things turned out with Panacea and Glory Girl?''



``I already quizzed her on this,'' Flechette said.



``I want to hear it from her myself.''



``That was Jack, not me,'' I said.  Flechette nodded, snorted just loud enough that she knew I'd hear it.  It was very `I thought she'd say that'.



``But you \emph{were} one of the last people seen with Glory Girl.  You \emph{were} sighted in Panacea's company,'' Clockblocker said.



``I tried to help her.  Talk to her.  We invited her to join the Undersiders, because she was in a bad headspace, she needed other perspectives beyond her own.  But she finished giving Glory Girl medical care after Crawler's spittle had burned through half her body, she refused our offers to help and refused Tattletale's suggestion that she fix what she'd already done to Glory Girl's head\ldots Tattletale knows the full story there, though I have suspicions.  The next time I saw her, she was talking to Jack, and he was getting to her, fucking with her head.  Stuff happened, I went after him, and it was the last time I saw her.''



``She had a freak-out, you know,'' Clockblocker said.  ``She was in a bad headspace, sure, but she was a good person.  Healed people I really care about when she didn't have to.  That's why I'm pressing you on this stuff, no matter what Miss Militia might put on my record or do to my patrol schedule.  Because Amy \emph{deserves} to have someone stand up for her, in her absence.''



``I'm sorry she freaked, but it wasn't my fault.''



``It was bad.  She took Glory Girl with her, you know.  When Gallant died, Vista saw the body.  When Aegis was mashed to a literal pulp by Leviathan, to the point that he couldn't function anymore, when he \emph{died}, despite his power?  I got to see the remains to verify for myself.  But Victoria Dallon was still alive and they \emph{didn't} let us see.  A select few adults and family members got to see her, they carted her off to a parahuman asylum and none of the rest of us got to say goodbye, because the end result was \emph{that} fucked up.''



``I didn't know, I'm sorry,'' I said.  ``But that wasn't my fault.''



``Fine.  I'll concede a point for you, then.  You tried, maybe.  One-naught.  What about Battery?''



``I was with Jack and Bonesaw, affected by the miasma, thought they were my friends.  Battery was giving chase.  Around the time I figured out what was happening, she got attacked by the mechanical spiders.  She was fine when I left her.''



``Assault blames you.  Probably why Miss Militia didn't have him riding in the van with us.''



``Okay.  If I'd been in a better headspace, I would have backed her up.  But there was the possibility Jack would get away, and the miasma--''



``It fucked with all of us.  Fine.  Let's call that another draw.  Can't judge you either way with that stuff in play.  Triumph?  His family?''



``Didn't know he was Triumph until we were in the thick of it,'' I said,  ``But I did it for Dinah.  It doesn't excuse it, but I did it for her.''



``How's that work?''



``To get into a position where I could free her, I had to get close to Coil.  He'd already clued into the fact that I was planning on betraying him if he didn't let her go, put the screws to me, basically.  Forced me to do what I normally wouldn't.''



``It had nothing to do with keeping control of the city?''



I hesitated.  ``I didn't say that.  I could try to justify it, explain how I really felt like I was doing more good than harm and what all that meant, but it would take too long, cover too many details I'm not willing to share, and I'm not a hundred percent convinced I'd buy it myself.  I'll concede that one to you.  Not in a position to defend or explain it.''



``One-all, then.  Let's talk Shadow Stalker.''



``We're back to that?''  I asked.



``She was an asshole, dangerous, didn't even \emph{like} her, but she was still a teammate of mine.  Some of your teammates might fall into that camp, so maybe you know how I feel.''



``Maybe.  But like I said, we weren't holding ourselves up as paragons of virtue.  You guys were.''



``Our focus right now is you.  \emph{You, }who drove Shadow Stalker into a corner, to the point where she flipped out on her mom and tried to hang herself with an electrical cord.''



What?



``\ldotsI'm not sure how to respond to that,'' I said.



``Do you feel \emph{bad} about it?  I'm genuinely curious.''



``I feel\ldots less bad than I should,'' I said.  ``But yeah.  It isn't nice to hear.''



``Because of what happened, because she was still reeling from the time she spent as your meat puppet, she attacked her mom, who called the authorities.  They caught up just in time to catch her in her room, electrical cord around her neck.  Cost Shadow Stalker her probation, meaning she got stuck in some parahuman detention center until she's eighteen.  And word is her mom doesn't want her back when she's finished the three-year sentence.  Last straw and everything.  Her life, put on hold, her family shattered.  Maybe she was damaged like you said, but you took her captive and tormented her until she went off the deep end.''



``I'm not happy she was pushed that far,'' I said, ``That's ugly.  You're right.  But getting her off the streets?  Yeah.  \emph{That's} worth it, at least.''



``What I don't get is\ldots \emph{why}?  Was the data from that computer really so important?''



``Coil needed it, and I needed Coil happy.  Either he'd like my work enough to free her on my request or he'd trust me enough that I could catch him off guard and help her escape some other way.''



``I'm sure Dinah would be \emph{thrilled} to hear that,'' Clockblocker said.  ``Some other girl's life ruined for her sake.  How \emph{does} a supervillain warlord react to that sort of news, by the way?  Finding out a heroine tried to hang herself?  Do you sit in your swivel chair, stroking your tarantula and pull off your best maniacal laugh?  One more enemy out of the way?''



``I didn't know,'' I said.  ``Not until you told me what happened to her.''



``That seems to be a recurring theme,'' he commented.  ``You do stuff, you have reasons, like your apparent feeling that, oh, it's okay because she was a violent personality, but you don't pay attention to the ending, to everything that comes after.  A whole lot of people have been screwed up and hurt in your wake, Skitter.''



``I react like you see me reacting.  I don't enjoy it.  No maniacal laughing here.''



``But you plan to continue doing what you're doing.''



``I'm not entirely sure what I'm doing in the future,'' I said.  ``Aside from stopping Noelle.''



``That's a good point to end this particular discussion,'' Miss Militia cut in.  ``I \emph{will} be adjusting your patrol route and noting this minor infraction on your record, Clockblocker.  I hope you're more or less satisfied with this discussion.''



``More or less,'' Clockblocker said, handing the combat baton to Miss Militia.  ``Unless our local Supervillainess-in-chief wants to pursue further debate.  I think I was ahead by one.  Two-one.''



``No, that's fine,'' I said.  I left it at that.  \emph{No, I'm not entirely sure I want to hear the full details on any of the other stuff}.  \emph{Quit while I'm only a little behind.}



If he knew me a little better, I wondered just how targeted those questions could get.



I'd killed a man, and I still didn't feel bad about it.  I didn't feel anything in particular when I thought about it.



In a way, I'd taken the perspective that I didn't feel bad about it because it wasn't wrong.  He was a bad person, irredeemable, and it had been the only option.



Except now Clockblocker's words and his \emph{tone} were resonating within me, and I was left just a little less confident about the conclusions I'd come to, in terms of the stuff we'd discussed and all the little events that had added up over time.  I'd made peace with who I was and who I was becoming in part because my peers were limited to other villains and civilians who I could dismiss because they didn't have the full perspective of life on the battlefield.  My dad was among those civilians, it almost pained me to admit.



I wasn't entirely certain I felt so peaceful now.  Most things, I couldn't imagine I'd really do them differently, given the circumstances and the knowledge I'd had at the time, but the decisions weren't sitting quite so easily as they had been.



It was several minutes before the van stopped.  Assault was the one who opened the door, and Clockblocker held the front door of the PRT offices open for me, in a very ironic manner.  My team was already waiting in the lobby.



I'd entered once as a prisoner and thief, once as an invader and kidnapper.  It was an eerie thing to be entering as ally to the good guys, when I'd never felt further from being one.





