





We had to take the elevator in two trips, due to the size of our group, and that meant splitting us up.  The heroes were too wary to leave any number of us unsupervised, whether it was on the ground floor or upstairs.



I entered the elevator in the company of Parian, Regent, Bitch, Bastard and Bentley, Miss Militia, Weld, Clockblocker, and Triumph.  It seemed to be an advanced design, the elevator offering so smooth a ride that I might not have been able to tell it was in motion if it weren't for the bugs elsewhere in the building.



We exited at the third floor.  I could use the bugs that had gathered near the waste bins or in the walls to try to get a sense of who and what was around me.  I recognized the area as the site where I'd entered via Trickster's teleportation: desks, cubicles, computers and paperwork.  I could sense some people heading into back rooms to rouse people who were sleeping in the office, on benches and in chairs.  All of the officers and out-of-uniform PRT operatives were gathering to look.



One of them stepped forward from the rest of the crowd.



``Deputy director,'' Miss Militia said, standing straighter.



``I'm too cynical to think this is an arrest, or to hope that it's anything more than another ruse,'' the Deputy Director said.  ``And I can't help but note these villains aren't in restraints.''



``It's not an arrest, and I \emph{hope} it's a trick,'' Miss Militia replied.



``You \emph{hope} it's a trick?'' the Deputy Director asked.



``Because I like the truth even less.  A \emph{new} class S-threat.''



Every officer in the room reacted, a general murmur punctuated with swearing and exclamations.



``Who?''



``An unknown.  Possibly a fourth Endbringer, not yet fully grown.  I'd like to get in contact with PRT thinkers to verify.''



``Waites,'' the Deputy Director called out, over the noise from the gathered police,  ``Doyon.  Get on the phone.  Patch them through to me as soon as you get hold of someone.''



``We should wake people up,'' Miss Militia said.  She glanced at the nearest clock, ``It's four twenty-four in the morning.  If this is real, we'll want the heaviest hitters ready to deploy at a moment's notice.  There's a chance this may be our \emph{one} chance to kill her.''



``You're killing her?'' I asked, quiet.



``No,'' Miss Militia said.  ``Nothing's set in stone.  But there's a \emph{chance} it may be our only opportunity and our only option.  If we're going to do it, I want to do it successfully.''



``No word from Director Calvert?'' the Deputy Director asked.



One of the guys in plainclothes spoke up, ``He's gone silent, sir.''



I didn't miss the fact that nearly a third of the local officers glanced my way.  We were apparently the prime suspects.  Which wasn't \emph{wrong}, per se.



The Deputy Director ordered, ``Militia, join me in the Director's office.  Triumph, see to it that the villains are detained and separated.  Interview rooms one and two for Regent and Skitter.  Conference room for Hellhound.''



I could sense Rachel shifting position.



``If I may make a suggestion, sir,'' Miss Militia cut in, ``I think we should put Skitter in the conference room?  She and Tattletale are our main sources of information.''



``Not complaining,'' I said, ``But Bitch, or \emph{Hellhound} if you want to call her that, may be more comfortable in my company.  Her dogs are their normal size.  If she uses her power, you'll be able to see.  Miss Militia already saw to it I was disarmed.''



``This sounds like you're positioning people for a maneuver,'' the Deputy Director said.



``No.  Just trying to keep things as copacetic as possible,'' I said.



``I'd okay it,'' Miss Militia said.



``Fine.  Hellhound and Skitter in the conference room-'' the Deputy Director paused as the elevator opened with nearly all of Brockton Bay's remaining parahumans.  ``Tattletale to the conference room.  Parian in the legal room.  Grue and Imp in interview room two.  Put police tape and a sign on the door with a notice of Imp's stranger classification to remind people why it's shut and \emph{staying} shut.''



``Hey!''



``Relax, Imp,'' Grue said.  ``You want to confirm this is alright, Skitter?''



``So long as my teammates go free when trouble starts,'' I said.  ``But yeah.  I understand the paranoia.''



\emph{And I think we could break out if we had to}, I thought.  I didn't say that part.



``This sucks,'' Imp commented.



``Suck it up,'' Grue responded.  ``Come on.''



We split up, with Rachel, Tattletale and I settling in the conference room, at the end furthest from the door.  Triumph stood watch, and the blinds were left open, leaving us visible to the countless officers who were now on their computers and phones.  There wasn't one of them who wasn't casting us suspicious glances every minute or so, or peering through the windows of the interview rooms at Regent, Grue and Imp.



I also noted the fact that there were nearly a dozen PRT officers fully suited up in their combat gear, complete with the full-face helmets, the chainmail-mesh covered body armor and containment foam sprayers.  They kept out of the way.  If I was using my eyes and I didn't have my swarm sense, I wouldn't have known they were there.



``Sorry, by the way,'' I told Triumph.



``The fuck you apologizing for?'' Rachel grumbled.  She'd settled into a chair, feet on the table, Bastard curled up in her lap.  One hand dangled, resting on Bentley's head.



``I attacked his home, remember?  Didn't know it was him, but Trickster threatened his family.  A fight broke out and I nearly killed Triumph.''



``They know?''  Triumph asked.  ``You shared the details already?''



``More or less,'' I said.  ``Bitch doesn't care and isn't the type to use it against you, and Tattletale would have figured it out anyways.''



Tattletale nodded.



``Fuck,'' Triumph swore.  ``Weld was right.''



``Anyways,'' I said, ``It\ldots there were better ways to do it.  So I \emph{am} sorry.''



``Didn't need doing in the first place,'' Triumph said, sighing.  ``I was prepared to risk my life the day I graduated from the Wards.  Knew what I'd be getting into.  Week I had clearance, I watched all the video we have of the class S threats.  Leviathan, Simurgh, Behemoth, Slaughterhouse Nine, Nilbog, Sleeper.  I knew what I was getting into.  So I'm not shocked or horrified at the attempt on my life.  What gets me is what you did to my \emph{dad}.  Set his career back years, if it's even recoverable, by forcing him to take that stance.  The whole thing, start to finish, was unnecessary.''



``He'll recover,'' Tattletale said, ``I'd argue his career was already pretty fucked after the way things went down, here.  Not saying he was to blame, or that he wasn't, but it's hard to graduate from mayor to governor when your legacy is a flooded ruin of a city.''



``It's not \emph{that} bad,'' I said.



Tattletale shrugged, ``Not if you're \emph{here}, but the photographers and reporters who are getting pictures and video footage of Brockton Bay aren't going to take pictures of the barely affected areas.  They're going to get the beaches, the south end and the crater.  Because that's what sells.  The people outside the city only see the worst bits.  When we're talking public perception, it's not what \emph{is}, it's the picture that's painted.''



``And the picture is of a handful of scary and powerful supervillains running a fucked up city,'' Triumph said.  ``Which is about to get more fucked up if you aren't pulling our legs.  So yeah, not a good legacy for my dad.''



``We have no reason to pull your leg,'' I said.



``Getting access to something \emph{else} that's confidential?  Covering your kidnapping of Vista so you're clear to use Regent's power on her later?''



``Why would we want \emph{her}?''  Rachel asked.



``She's strong.''



``Bitch's question is a good one,'' Tattletale said.  ``Yes, Vista's strong, but why would we want her?  It'd be putting ourselves at risk, for no particular gain.  If we wanted raw power, we'd have kept your cousin.  There's nothing left in the city that we want or need, so it's not like we really need her assistance to get a job done.  We have money, we have resources, and anything that's worth anything is destroyed or taken by now.''



``Then what \emph{do} you want?'' Triumph asked.



``Security.  We have all of the basics.  Shelter, food, warmth, companionship, money.  Anything we do from here on out's going to involve better securing ourselves where we're at.  We want to stop visiting villains from getting a footing anywhere in the city unless they're joining us.  Keep the peace so we keep \emph{you} guys off our backs.  I wouldn't mind a system like the Yakuza of Japan's yesteryear, where we support and involve ourselves in local business, \emph{legally}, to the point that nobody will be able to shake us.''



``That's terrifying,'' Triumph said.



``Why?  Because we're \emph{bad}?  Ooh, spooky,'' Tattletale waggled her fingers at him.  ``If we do it right, we won't have to extort anything from the locals.  We can do more to stop the drug trade than any of your guys.  Then we disappear into the background, make enough money off the side benefits of our powers and investments to live a life of comfort.  Mobilize only if and when there's a new threat.  Build trust with \emph{you} guys, ensure that any new parahumans go to either your group, go to ours, or they get dealt with some other way.  Ensure that anyone like \emph{Hellhound} who needs more elbow room or freedom is somewhere they're comfortable, where they won't do any real harm.''



``And she's okay with that?'' Triumph asked,  ``Being benched?''



``Give me my dogs, don't bother me, don't get in my face, I'm okay with whatever,'' Rachel said.  Her arm was moving.  It took me a second to realize she was scratching Bastard.



``Calmer than you were a week and a half ago, if that's the case,'' Triumph said.



``Dunno,'' Rachel replied.  ``That was then.  This is now.''



Triumph sighed.



Weld and Clockblocker joined us.  Clockblocker handed Triumph a can of coke or something like it.



``They behaving?'' Clockblocker asked.



``Pretty much.  Tattletale mentioned Dinah, but it wasn't to fuck with me.  We were talking about their master plan, if you can call it that.  Not much else.''



Clockblocker looked at me.  ``Skitter and I had a discussion on the way over.''



``And you won't have another,'' Miss Militia cut in.  She'd stepped out of the Director's office next door and into the doorway.  ``We're not here to socialize.  We got in touch with some thinkers.  Eleventh Hour says he gets an `eight'.  Appraiser's read says we're `purple'.  Rule for any pre-situ call is we get three points of reference,  going by thinkers alone, that means a third thinker.  The first they were able to get in touch with was Hunch.  Your old teammate, Weld.''



``Didn't think he rated, yet,'' Weld said.



``Chief Director Costa-Brown gave the a-ok, and Hunch says it's bad.  All together, we're calling this a threat level A.''



``No shit.  The Undersiders are for real?''  Triumph asked.



Tattletale didn't wait for him to get an answer, ``That's threat level S.  S-class.''



``The Chief Director of the PRT determined it was an A-class threat.''



``Bullshit,'' Tattletale said.  ``S-class.  I know Appraiser offered a purple-velvet diagnosis for his previous ratings on Endbringer attacks, so that's not the reason it's so low.  Eleven's score of eight has to be above the seventy-five percent mark, and an answer as vague as Hunch's is going to be a seventy-five percent exact, as per section nine-seven-six, article seventy-one.  That's three values that \emph{have} to be above the threshold for declaring a threat level S situation.''



``How the hell do you know all that?'' Weld asked.



Tattletale waved him off.



``The Chief Director made the call.  We're standing by it,'' Miss Militia said.



``We're talking \emph{class-S, }even if you ignore pre-situation verification.  Section nine-seven-five, article fifty-seven.  Classifying high level duplicators and villains who operate to any exponential degree.  Nilbog and Simurgh both count, and Noelle does too.  If the powers generate more instances of power generation or recurring effect in an epidemic pattern\ldots''



``She's not a \emph{self} duplicator,'' Miss Militia said, ``And yes, she's creating powers, but they're copies of \emph{other people's }powers.  They're not exponential or self-recursive in effect.''



``You're splitting hairs.''



``And,'' Miss Militia said, ``She doesn't create more powers \emph{on her own}.  She has an intrinsic requirement of needing contact and time to absorb.  She doesn't meet the criteria as they stand.''



``Still splitting those hairs,'' Tattletale said.  ``Her threat level zooms up to S as soon as she gets her hands on anyone who can enable something like that.  Like, say, \emph{any tinker}.''



``I don't know why we're even discussing this, when you seem to have our operations manual memorized and you're capable of realizing it for yourself,'' Miss Militia said, ``but it doesn't bear dwelling on.  The difference in our response to a class A crisis and a class S one is minor at best.  Some tertiary protocols change, we won't necessarily have Alexandria, Legend or Eidolon assisting, and there's no penalties for anyone who subscribed to the critical situation roster if they sit this one out.''



``Which they will,'' Tattletale said.  ``You're ignoring the fact that people are inherently selfish.  It takes \emph{something} to shake them from that reality, and that's not common.''



``I think you're underestimating the inherent \emph{good}\emph{ness} of people who dedicate their lives to heroism.  I know for a fact we have ample volunteers already informed on the situation.  They're en route.''



``If the heroes aren't showing in full force, others won't either.'' Tattletale said, ``And there's no epidemic protocols with a class-A.''



``We have \emph{one} tinker,'' Miss Militia said.  ``Kid Win.  Armsmaster is no longer on the premises.  We have no duplicators.  The risk is one we can control, either through the organization of our forces or turning any combatants with problematic interactions away.  Epidemic protocols are unnecessary.''



``Armsmaster escaped, you mean,'' Tattletale said.  ``And it won't be that easy.''



``Maybe not, but that's the word from above.  I'm not interested in debating this further, Tattletale.'' Miss Militia said.  She turned her head slightly toward me, clearly expecting me to comment along the lines of what I'd said in the containment van, about authority tying one's hands.  When I didn't rise to the challenge, she said, ``We're having a strategy meeting in a matter of minutes.  The first phase of the response will be teleporting in momentarily, but our best mass-teleporter died in the Leviathan attack, and the process is slow.  I'll be releasing the rest of the Undersiders to join you soon.''



``As soon as you have enough extra bodies to watch us,'' Tattletale commented.



``Yes,'' Miss Militia said, terse.  She looked at the three young heroes who had gathered at the wall by the door.  ``Be good.  Excuses or no excuses, it looked bad when we had the \emph{last} incident with a break in the truce.  Don't let Tattletale provoke you, don't provoke \emph{them}.''



``You can't blame them if they get emotional,'' Tattletale sighed.  ``It's only natural, three young men, three young women, a possibility of Capulet-Montague forbidden love between hero and villain\ldots''



``My warning goes for you too, Tattletale.  I already instructed Triumph to shout at the first sign of trouble.''



``I'll be angelic,'' Tattletale said.



``Good.  You should also know that Parian is leaving.  She asked me to tell you, and to let you know she'll be at her territory.''



Parian was gone?  \emph{Shit}.



``I wouldn't have let her go,'' I said.  ``For a lot of reasons.''



``It's unfortunate, I agree,'' Miss Militia said, ``But we're not in a position to stop her, short of fighting her.  She was adamant about not wanting to participate in this fight.  Flechette is escorting her back.''



``And however Noelle found Vista, she might find Parian and Flechette and target them the same way,'' Tattletale said.



``Maybe.  They both have devices to alert us.  In the worst-case scenario, they can inform us if something's happened.  Now, if you'll excuse me, I need to prepare.''



Miss Militia didn't wait for a response.  She was already striding down the hall, gesturing to get someone's attention.  Someone too small and too young to be a cop.



The three boys at the other end of the long table started talking among themselves.



``This is falling apart before it begins,'' Tattletale commented.



``I get the impression Miss Militia's spooked,'' I said.  ``She's tense.''



``Anyone would be,'' Tattletale replied.  ``Doesn't help that the last Endbringer fight ended her predecessor's career.''



I nodded.



``Our muscle's going to suffer in this fight,'' Tattletale said.  ``Your bugs, Bitch's dogs, they can't hurt her, if she absorbs things on contact.  Not unless we want clones of Bitch's dogs running rampant.''



``The heroes have long ranged fire,'' I replied.  ``Kid Win, Miss Militia, Triumph.  So Bitch and I adopt a support role.  The dogs get our key players around the battlefield, if Bitch is willing.''



Rachel grunted something that could have been agreement.



``And I might be able to tie Noelle up without the bugs touching her.  Grue can slow her down, Regent could do the same.'' I finished.



``Regent couldn't use his power against Leviathan.  Can you imagine him getting Leviathan under control?''



``I'd rather not,'' I admitted.  ``There's a sweet spot as far as rep goes.  Having a pet Endbringer puts us in the `too scary to be allowed to live' category.''



``We'd have to do what the Slaughterhouse Nine do, win frequently enough against high odds that people can't afford the losses.''



``Would mean we have to go mobile,'' I said.  ``So we have time to recuperate while the enemy tries to track us down.  Anyways, enough `what if'.  Let's get back on topic.''



Tattletale nodded.  ``Imp?''



``For this coming fight?  Rescue,'' I said.  ``The enemy won't target her, they might not target anyone she can get in contact with.  Fallen allies, captives, Imp gets them to safety.''



Tattletale nodded.  The tone of her voice shifted fractionally as she said, ``You guys can chime in at any point here.''



The young heroes had stopped talking and were listening in.



``I don't know what you want us to add,'' Clockblocker said.



``Interactions,'' I said.  ``Maybe we put you on Bentley's back.  We won't have to kill Noelle if you can tag her.  We'll be able to keep her frozen long enough for us to erect some form of containment.''



``Me?  On the dog?''



``You scared?'' Rachel asked.



``I think \emph{anyone} would be a little scared.  You can't tell me they aren't a little intimidating.''



``Your power nullifies any threat they could pose,'' I said.



``If it closes its teeth around my arm, the fraction of a second it takes my power to kick in is going to buy it time to dig in just a little.  Jaws clamped on my arm, I freeze it, sure, but then every time it unfreezes, it closes a \emph{little} more before I can freeze it again.  No thank you.''



``He's scared,'' Rachel said.  She scratched the top of Bastard's head, and I realized she was talking to the wolf cub that was sleeping in her lap.  ``You're the stuff of nightmares.''



Clockblocker snorted, then got caught up in a murmured conversation with Weld and Triumph.  They were facing our way as they talked.



I tried to ignore them, focused on taking deep breaths, controlling the intake so I wouldn't start coughing and humiliate myself in front of the local heroes.



``You okay?'' Tattletale asked.



``Coughing less.  I feel like I've maybe got the worst of it out of my lungs and throat.''



``I meant \emph{you}.  You've been quiet.  You weren't saying as much as you normally might when I was talking to Miss Militia.''



``Thinking.''



``Important you keep doing that,'' she said.  ``But not if it's getting you like this.  Unless you're putting together a master plan.''



I shook my head.  ``No plan.  Just fatigue and-''



I stopped.  Each and every officer in the next room was turning their heads.  I used my bugs to feel out the subject.  A hood, with the warmth of a faint natural glow from beneath, with the same effect around his hands, with his loose sleeves.  I noted that a glass helm like the one Clockblocker wore fit over his face beneath the hood.  People went out of their way to clear out of his path, to such an extent that I might have thought they were in front of an elephant and not a man.



Eidolon entered the conference room and grabbed the seat just to the right of the one at the far end of the table.  He swept his cape to one side before he sat down.



``Didn't think you were coming,'' Tattletale said.  ``With it being \emph{just} a Class-A threat.''



``The infamous Undersiders,'' Eidolon spoke.  His voice reverberated slightly, an effect similar to Grue's.



``And the famous Eidolon,'' Tattletale retorted, ``while we're doing the reverse-introductions.      I \emph{thought} I told Miss Militia that we shouldn't bring in anyone we can't beat in a fight.''



``Don't concern yourself over it,'' Eidolon said.  ``I can render myself immune.''



``We won't know until it happens,'' she replied.



There was a pause.



``Tattletale.  Are you looking for a chink in the armor?''



``You can't blame me, can you?  If we wind up having to fight you, then it might be all over.  So I'm gathering intel.''



Eidolon didn't reply.



``Okay, sure.  Fine,'' Tattletale raised her hands in surrender.  ``It's cool.''



Eidolon turned away to follow the murmured conversation between Weld, Triumph and Clockblocker.  Tattletale rested her elbows on the table, rubbed at her eyes.



``Tired?'' I asked.



``Exhausted.  Been using my power all night, my head's throbbing, and this whole business with Noelle hasn't even started.''



``Take a nap,'' I suggested.



``No time.  And I \emph{do} want to make sure I have some ideas in advance, for anyone we might have to face.  Noelle is going to target Eidolon.  If we fight him, we'll have to use his weaknesses against him.''



``Tattletale,'' Eidolon cut Clockblocker off mid-sentence, his voice carrying across the room.  ``Could you elaborate?''



``Don't worry,'' she said, ``No weaknesses you don't already know about.''



``Is that so?''



``You're losing your powers,'' she said.  ``Not fast enough that it matters \emph{today}, but enough that the difference is appreciable.''



It was hard to read Eidolon's body language with the few bugs I'd permitted myself.  He was leaning forward slightly, and his upper arms pressed against the fabric of his costume as he flexed or clenched a fist.



``And how would you know this, if it were true?''



``Because any other day, with you heroes being as short on teleporters as you are, you'd be helping bring people in.  You're conserving your strength.  It might even be a long term fear, like you've only got so much power to use over your lifetime before it's all spent.  Candle that burns twice as hot, or something.''



``Simple deduction?  Did you consider that I am not teleporting people because there's a shortage of volunteers?''



``That would contradict what Miss Militia said, and she wasn't lying.  And it doesn't fit the overall picture.  Alexandria-''



Eidolon slapped his hand down against the table.  A forcefield expanded from the impact site, forcing Rachel and I out of our chairs and against the wall.  I slumped down to the ground, grabbing my rib, and coughed painfully.



The forcefield had kept Rachel and I out, but Tattletale was inside with Eidolon.  The sounds from within were muffled.



But I had bugs on both Eidolon and Tattletale, and I could almost make out their words.



Tattletale was speaking.  ``\ldotsreason you \ldots this situation a class-A threat isn't because it doesn't fit.  \ldotsdid it is because Alexandria wanted an excuse not\ldots \ldots  You came because you needed to prove something to yourself.  Test \ldots measure of your power in a \ldotsnse situation\ldots work best when\ldots danger.  This is best challenge you'll have\ldots''



``\ldotstreading dangerous waters,'' Eidolon spoke.  There was no growl in his voice, no anger, irritation or emotion at all.  Only calm.  It made him easier to understand.



``\ldotscan live with danger, \ldots it's \emph{interesting.  }Awfully interesting\ldots why Alexandria's not coming\ldots \ldots \emph{me?}  \ldotssecret.''



Eidolon said something, but his tone had changed and I wasn't able to switch mental gears fast enough.



``\ldots\emph{you?}''  Tattletale asked. ``\emph{Years\ldots}-''



``The fuck!?'' Rachel snarled.  Bentley growled as if to accompany her words.  He was already growing.



``Relax,'' I said, before I started coughing again.  ``They aren't fighting.''



``He knocked me over!''



I could see Miss Militia and Assault at the other end of the room, but the forcefield bubble was blocking us.



``What happened!?'' Miss Militia shouted.



I tried to respond, coughed instead.  My voice was weak with the fresh rawness of my throat as I did manage to utter a reply, ``Eidolon flipped\ldots''



``Eidolon attacked!'' Rachel yelled.



``Did she provoke him?''  Miss Militia asked.  Her gun was raised.



``No,'' I managed only a whisper.



The forcefield winked out.  Eidolon was still sitting, he hadn't moved except to slap the table with his hand, but Tattletale was standing.



``Just wanted to have a private conversation,'' Eidolon said.  ``I'm sorry.  I'll be getting some fresh air.''



With that, he stood and strode out of the room.  He made his way to the stairwell and I could track him moving to the roof.



I picked up my chair and sat, still coughing intermittently.  Rachel was still standing, and her dogs were still growing.  I gestured for her to sit.



She just glared across the room.



I gestured again, but the force of the motion made my chest hurt and I started coughing.  Before I recovered, Rachel sat with an audible thud.  She kicked her boot against the edge of the table, hard, and left it there.



``What did you do?'' Miss Militia asked.  She was facing Tattletale.  I could see the other Undersiders behind her.



``Was just commenting that it seemed odd he wasn't helping you guys out with teleporting people in,'' Tattletale said.



``You said more than that,'' Weld noted.



``I'm tired, he's tired, we talked it out.  All copacetic,'' Tattletale said.  She leaned back and stretched.



``I'm not so sure,'' Miss Militia said.  ``Skitter, are you alright?''



``Recent injury,'' I managed.  ``Will be fine in a minute.''



Miss Militia nodded.  Not much sympathy, but I couldn't blame her.  ``Then let's get things underway.  Everyone, please get seated, or find space to stand.''



Grue, Regent and Imp joined us, and Grue set his hands on my shoulders as he stood behind me.  He rubbed my exposed back where the armor panel was missing as I coughed hoarsely once or twice.



I counted the people in costume with my swarm.  It wasn't nearly as many reinforcements as we'd had against Leviathan.  I saw Chevalier and Myrddin, but didn't recognize anyone else.  There were the Wards and Protectorate members from Brockton Bay, with perhaps twenty more.



``Tentative ratings, based on what we know, we have her down as a brute eight, a changer two and a combination of striker and master with a rating of ten.''



``Too low,'' I heard Tattletale murmur.



I suppressed a cough, managed only a choke.  It drew more attention to me, and I couldn't shake the feeling that everyone was already paying way too much attention.  I was wearing my older costume, and somehow felt more juvenile, more exposed.  I didn't have the covering of bugs over the exterior of my costume like I was used to, either.



``Her ability allows her to create clones of anyone she touches.  The PRT office believes she's a class-A threat, but \emph{Tattletale's} expectation is that this individual has the potential to become an Endbringer.  We're moving forward with extreme caution.



``Our primary issue at the moment is that we can't yet locate her.  She has one hostage, a young member of the Wards.  The girl was attacked en route to her home.  Locating our target quickly is \emph{paramount}, but we should also be careful to avoid giving her a chance to use her power on us.  For the time being, we will be operating with the same protocols and plans that we employ against Hadhayosh.  Hit and run, maintain a safe distance as priority number one, and employ continuous attacks.  We'll be dividing you into teams-''



Miss Militia stopped short as an officer pushed his way through the people near the door, Chevalier included.  He handed Miss Militia a phone.



She turned around and pressed a button on the wall.  The faux-wooden panels separated to reveal a widescreen television.



It flickered on.



``\emph{Her}?'' Kid Win asked.  ``\emph{That's} the class-S threat?''



``She's bigger than she looks,'' Tattletale commented.



I was disappointed I couldn't see.  I tried looking at the screen with my bugs, but they saw only a rectangular glow.



``Quiet,'' Miss Militia said, ``It's a webcam feed.  I'm setting it so we'll be transmitting audio only\ldots Hello, Noelle.''



``Who is this?''  Noelle asked.



``She \emph{talks},'' I heard someone whisper.



``Miss Militia,'' Miss Militia said, louder.



``The gun woman.  Who else is there?''



``Other local heroes,'' Miss Militia replied.



``Oh.  There aren't more?  The Undersiders didn't get in touch with you?''  Noelle sounded funny.  Her voice was hollow, almost disappointed.



``It's just us right now.''



``Because I \emph{smell} more,'' Noelle said.  ``Which makes it hard to believe you.  But you can lie if you have to.''



``You can smell us.''



``Not \emph{you}.  But it \emph{doesn't matter},'' Noelle's voice broke.  She stopped.



``Are you there?'' Miss Militia asked.



``I'm here.  I was telling you it doesn't matter.  I only called because\ldots I killed her.  The space-warper.  I'm so bad with the names.  So many names for you capes.  I only ever paid attention to the powers.''



``You killed Vista,'' Miss Militia said.  ``Why?''



``Because I could.  Because I was hungry, and I'd already used her up.  See?''



There was a brief pause, then a number of gasps and breathless words all at once.  One of my bugs caught a noise from Clockblocker, deep in his throat.



Grue leaned close, whispered in my ear, ``\emph{Five Vistas.  All but one of them have faces more like masks than skin and muscle.  Hard, rigid.  Wearing borrowed clothes, not costumes.  The fifth one might be taller than I am, and her bones look curved.''}



I nodded.



There was a thump from the microphone on Noelle's end, presumably as she turned the camera back to herself.



``Just wanted to let you know that.  I'm sorry.  This isn't like me.  It's the stuff that's growing on me.  I have my memories, and when I think, it's always my thoughts, but it feels like it's taking over my \emph{subconscious}, and when it wants something the hormones and adrenaline flood into \emph{my }body and \emph{my} brain, so I feel what it feels.  Twists the way I think.''



``Why \emph{Vista}?''



``She was alone.  And could smell how strong she was.  Read about her online, too.  Internet was all I had for a long time.  Now I've got \emph{them}.  They're pretty obedient, and it's nice to have company.  I haven't had any physical contact with anyone for a while, and they like giving me hugs.  Except the sixth.''



``Sixth,'' Miss Militia said.



``Not as obedient.  She ran off.  Gibbering something about killing her family.''



Miss Militia thrust her index finger toward the door, and the Wards were gone in a flash, running for the stairwell.



``Can we negotiate?''  Miss Militia asked, her voice oddly calm given the ferocity of the gesture and the threat against one of her colleagues' family.



``Not really a negotiation\ldots but I can offer you a deal.''



``What's the deal?''



``Kill the Undersiders.  Or hand them to me so I can torment them before I kill them.  You can do it any time you want to.  Just\ldots knock them out, or hurt them, or find a way to tell me where they are.  If it's a choice between hurting one of \emph{you} or hurting one of \emph{them}, I'll hurt them.  I promise.  If I've taken someone hostage, you probably have a little while before the hostage is dead.  Just know that I'll trade you any of my hostages for any Undersider, any time, any situation.  When the Undersiders are all dealt with, I'll sniff out and kill all of the clones I've made, then I'll let you try to kill me.  Or imprison me.  Do whatever.  I don't care anymore, because I don't think I'll be \emph{me} much longer.  I don't think I'm even \emph{me} right now.  Not the me I was\ldots I'm rambling.



``They took away my only chance.  My only chance to get well.  Until they've paid for that, I'm going to make this \emph{hard} on you, heroes.  I don't think I can die, and I don't think I'm that easy to stop in other ways.  I'll hunt you down, I'll copy you until you're all used up, let your copies ruin your reputations and your lives, and then I'll eat you.  I'll do it to each of you, one by one, until you realize it's easier to go after the Undersiders than to come after me.  Give me my revenge, and this ends.''





