





The television screen went dark.



Transmission over.  Damage done.



``Well,'' Tattletale said, ``Funny thing is, that was only the \emph{second} worst thing she could have done to screw us over.''



``That so?'' asked one male cape I couldn't identify.



``Oh yeah.  I was worried she'd disappear for a few days or weeks, leave us to go looking for help.  Then we'd look crazy when she didn't show, and whatever concessions we'd made to get you on board would cost us\ldots like how you have us in custody right now.  Either she's not as smart as Ballistic implied, or she's feeling some kind of pressure.  I'd lay odds she's losing the inner struggle for self-control.''



Someone slammed his hands down on the end of the table, interrupting her.  I sent bugs in that direction to identify the speaker.  ``Does it fucking matter?''



My bugs traced his armor.  Assault.



``It matters,'' Miss Militia said.



``This monster killed one of the good guys.  One of our \emph{best}.  We let it slide when the Undersiders took Shadow Stalker.  We accepted it when the Nine got to Glory Girl and Panacea.  When they killed \emph{Battery}.  We let the Undersiders take the Director, and they may have taken the man who's \emph{replacing} her.  Are we \emph{really }going to ignore the most obvious option here?''



``You're saying you want to turn the Undersiders in.''



``They broke the code.  They'll break it again.''



``And now we're effectively on trial,'' Tattletale said, ``When we should be hunting her down.''



``Which may be exactly what she wanted,'' Grue added.



``You may be giving her too much credit,'' someone said.  I was having trouble keeping track of who was talking.  There were too many people in the room, and gathering more bugs would potentially give someone cause to think I was massing a swarm in anticipation of a fight.



Not to say I \emph{wasn't}.  I'd been collecting a swarm, hiding them in shadows and beneath cars.  I drew them closer to the building, as surreptitiously as possible.



It was strange, to have more awareness of the world beyond the local PRT headquarters than I had of the room I was currently in.



``Did you miss the part where there were \emph{six} Vistas?''  Tattletale asked.  ``She's a pain to deal with, trust me.  If anything, you're \emph{under}estimating Noelle.''



``I'm forced to agree.  Let's \emph{not} underestimate any opponent,'' Miss Militia said.  ``I'm going to put in my recommendation right here, with full knowledge that there are several people present who outrank me, and I will extend my full cooperation if they should decide on a different route.  I think we should put old issues aside and accept any assistance the Undersiders are willing to offer.  With what happened with Vista, it's all too apparent how this situation could get out of control, with each of us fighting friends.''



She paused, and nobody cut in.



Miss Militia continued, ``We treat this situation as we would an Endbringer attack.  Our side is smaller than we might hope for, but our enemy is more vulnerable.''



She looked to one man, and I realized she was checking with the Deputy Director.  Her superior, so to speak.



He offered a single nod.



``I agree,'' Triumph said.  My bugs were still on him, from earlier.  ``But we'd need you on board, Assault.''



Assault was standing, hands still on the table.  He didn't respond.



``We can't get the Undersiders on board if they're wondering if we'll backstab them,'' Triumph said, calm.  He wasn't someone I'd anticipated as an ally, here.



``You mean like they backstabbed us during the Leviathan attack?'' Assault asked, his voice a growl.  ``Broke the truce?''



``What?'' I couldn't stop myself.  My voice sounded so small and feeble, between the recent spell of coughing and the lack of bugs to augment it.  I wished I could have conveyed more of a presence.  How to word it so it didn't sound like feeble protests?  ``I think you've been\emph{ }grossly misinformed.''



Fuck me, I sounded like Coil.



``Would Battery want you to put your feelings and prejudices before duty and the safety of this city?''



Assault slowly turned to Miss Militia.  ``You want to play that card?''



``I'll play it.  And if the Undersiders decide to play it fast and loose with the rules again, I'll be right there beside you, ready to see them answer for it.''



``We've talked about that before.  Nothing came of it,'' Assault said.



``This time,'' Miss Militia said, ``Given precedent, the stakes and the dangers posed by villains unwilling to follow the written and unwritten rules of the cape community, I'd be willing to argue and testify for a kill order.''



I felt a chill.



A kill order.  It was what they had in place for the Slaughterhouse Nine.  No holds barred, official heroes would be allowed to shoot us on sight.  Any villain or vigilante that came after us would be allowed to go free with only a brief questioning for the paperwork after killing one of us.  To top it off, anyone would be able to donate or post amounts for our heads; amounts would be added to running totals.  We'd be waiting jackpots for any bounty hunter or assassin looking for a big score.



I wondered if any of Coil's wealthier investors or contacts would hold a grudge.



There were any number of arguments against her statement.  We'd done good.  Even Clockblocker had been willing to argue that the calls I'd made weren't entirely without merit.  I could have pointed out that any number of people in my territory would argue I was a force for good, and that it was ludicrous that \emph{we} were the ones being held to this standard when \emph{they'd }been at fault for Armsmaster's breaking of the truce.  Armsmaster, who had gone free because of hero's prerogative.  But that same bias meant things had been twisted around, and apparently popular sentiment held \emph{us} at fault for the breaking of the truce.  It was an unpleasant surprise.



Hell, to give us the `one last chance' line with a situation where there was every possibility of friendly fire?  It was tying our hands, putting us at mortal risk one way or another.



``I'm\ldots willing to accept that,'' I said, suppressing every argument and every bit of indignation I was feeling.  I looked in the general direction of my teammates.  ``If my team is.''



``You're the boss,'' Tattletale said.  She was quick enough on the draw that I suspected there was a reason she'd said it.



``Yeah,'' Grue said.  My bugs caught Imp and Regent nodding.



Rachel's response was last.  ``Whatever.''



``Well then,'' Tattletale said.  ``Now that that's settled, in the spirit of being allies, I have some news.''



``News?''  One of the unfamiliar capes asked.  A woman with a deeper voice.  ``\emph{Good }news?''



``Oh, it's terrible news,'' Tattletale said.  ``Noelle's lying.''



``About what?'' Miss Militia asked.



``About Vista being dead.''



``That's \emph{terrible} news?  Is she in danger?''  Triumph asked.  I sensed him leaning forward to get a better view of Tattletale, past the crush of bodies at the end of the room.



``No.  I can't say how Vista's doing, because I don't know the specifics on Noelle's power, but she was trying to mislead us, talking about how she'd \emph{use us up}.  Too much stress on it.  If she'd only said it the first time, I'd be more inclined to think it was part of her stream of consciousness, but then she hammered it in, used it to threaten us.  It felt forced.  Didn't ring true.''



``Can we believe her?''  This from another unfamiliar cape, a man.  It was apparently directed at Miss Militia.



``She's\ldots frequently correct,'' Miss Militia said.



``Vista's alive and Noelle's trying to keep that secret?  What's so terrible about it?''  Triumph asked.



``Because it means she's capable of producing \emph{more} clones.  She's capable of keeping Vista captive somewhere, continually producing agents to sow destruction and apply the kind of pressure she was talking about, and she's lucid enough to recognize that fact.''



``How the hell do you keep Vista captive?''



``People,'' Tattletale said.



``Then let's wrap this up fast.  Essential details only,'' Miss Militia said.  ``Any objection to me taking point?  Eidolon's not usually comfortable with it, and I'm the ranking parahuman in Brockton Bay.''



There was no dissent.



``Then we're splitting up into teams.  Stick with the teams you arrived with.  Best to fight alongside people you know.  Standard stranger countermeasures are in effect with the clones.  I'll assume they retain the memories of the original, based on what she said about the clone going after Vista's family?''



``They do,'' Tattletale said.



``Then we're restricted to visual ID checks only.  No passwords.  I already got in contact with Dragon.  She's on a mission and will only deploy here if it's absolutely essential-''



I caught a sigh from Tattletale.



``-But she's set the armbands up for the coming conflict.  They'll display a green screen up until you remove them, and the screens will flash and identify other armband wearers at a range of fifty meters.  Be vigilant.  Keep track of every one of your teammates, maintain a visual, no splitting up.



``Chevalier, take your team, follow after my Wards.  If she can detect capes, we'll need to assign her a thinker classification, and we'll need to assume that any isolated groups are at risk.  Undersiders?  Take Myrddin's Wards and pursue Flechette and Parian.  Ensure they aren't intercepted.  The rest of us will track down Noelle.  Any indications about her location from the video?''



``Yes, but there's no point,'' Tattletale said.



``You know her location?''



``I know her location as of the time of the call, but she'll be moving already.''



``Where?''



``The west end.  By the mountains.''



``She went from just east of Downtown to the west end?'' Miss Militia asked.



``I'd stake money on it.  But again, it's no use.''



``It doesn't make sense in terms of timeline,'' someone said.  He sounded slightly nasal.  ``The distance covered-''



``Think about it,'' Tattletale said.



``Vista,'' Miss Militia supplied.  ``She had Vista's power.  And she \emph{will} have that power at her disposal for the duration of this conflict.''



``And Noelle's fast,'' Tattletale said.  ``Put those points together and she's \emph{highly} mobile.  Ergo, she isn't going to be anywhere near where she was.''



``Good intel.  In the interest of finding her, I'd like you to accompany my group, Tattletale.''



``No can do.''



``\emph{No}?''



``I was just about to say I was wanting to stop by my headquarters.  I have a few theories on how we could handle this situation, and one off-the-wall idea that needs some verification before I do anything about it.''



``Nothing that puts any of us at risk?''



``No.  It mostly involves the other Travelers.  But I think it's worth pursuing.''



``If she comes after you-''



Tattletale cut her off.  ``She will.  I'll join the Undersiders and the Chicago Wards as far as going to Ballistic's territory to fill him in, ensure he knows that she may come after him.  I'll see if I can't bribe him into coming with me.  It'll be a narrow window of time where it's just me, him and hopefully his flunkies.''



``You make a high value target,'' I said, ``Especially with Ballistic in tow.  She wants you dead, and she wants \emph{his} power.''



``I have ideas.  Don't worry about me.'' Tattletale turned.  ``Miss Militia, I'll be in touch by phone, so you know where you're going.''



``Fine.  I'm ordering more capes to patrol the area around you, then, if you're sure you'll be a target.  Are there any other isolated parahumans in the city that we aren't aware of?''



``Scrub,'' I said.



``He's working under Ballistic,'' Tattletale said.  ``I'll get him on board by any means.  He's one of the few people, short of Flechette, who can deal guaranteed damage to an Endbringer or Endbringer-Lite, and I have ideas about him and how I could use him.''



``Scrub?'' one of the visiting capes asked.  The deeper-voiced woman.



``Uncontrolled matter-annihilation bursts in his immediate vicinity,'' I said.  ``Ex-member of the Merchants, a local gang of dealers and users.''



``Blaster-eight, easy, if not a straight ten, despite his relatively short range,'' Tattletale supplied, ``But I'm not sure he does what Skitter thinks he does, and that's why I want to talk to him.''



``See to it,'' Miss Militia said.  ``Anyone else?''



``Circus, Leet, Uber,'' Grue said.  ``They were leaving, but-''



``They're dead,'' Assault said.



``They're very much alive,'' Tattletale retorted.  ``And they would have gone \emph{west} to leave the city.  The same direction Noelle went after targeting Vista.  I think that speaks for itself.''



Miss Militia nodded.  ``It does.  If anyone has any questions, communicate them while on the move.  Go!''



The capes began flowing out of the room.  We had seated ourselves at the furthest point from the door, so we were stuck inside until the way was clear.



A small group of younger capes hung back.  Miss Militia had left us a contingent of out-of-town Wards.  I couldn't get much of a sense of them just with what my bugs could give me on their costumes.  They probably weren't a full team from a city as big as Chicago; they'd be limited to the ones who'd agreed to fight an unknown, A-class threat.  Three boys and a girl.  They were watching us, and I couldn't even guess at their expressions without the ability to see \emph{or }feel things out with my bugs.



I was getting tired of this, and my fatigue was wearing on my already thin patience.



``Bitch,'' I said.  ``Do me a favor and clear that window?''



She didn't respond, but she didn't hesitate either.  She was on her feet as soon as she'd lifted Bastard off of her lap, and kicked the plywood free of the frame before anyone could protest.



I brought every bug I'd had outside the building into the room.  They swirled around me, the Undersiders, and the handful of capes on the far end of the room.  I could sense three of the four Wards getting into fighting stances, noted how two of the boys and the girl shielded the one other boy, forming a loose triangle formation between him and us.



The movements of the bugs gave me the ability to feel them out, drawing a complete map of what they were wearing and carrying.



The boy in the very front, the tallest and largest of them, would be a tinker.  The rods that supported his heavy gauntlets were oiled, suggesting they were pistons, and I noted the presence of blunt-tipped spikes inside his gauntlets.  The setup wasn't unlike the blades in Mannequin's arms, but these weren't extending into his body, and I somehow got the impression they were intended for something very different.  His armor was heavy, supported more by engineering than by his own strength, and his helmet covered his face, but not the back of his head, with a single lens on a telescoping nozzle, dead center.



The other boy in front was narrower, with flowing clothes.  He sported a surprising lack of equipment and weaponry.  It gave me the sense of someone who thought of their body as a weapon.



The girl was similar, but I did note that her gloves were reinforced for striking, a framework of some sort of metal, with rivet-like bumps over each knuckle, each etched with a fine design I couldn't make out and metal filigree feathers at the edges.  She had padding with a similar design and near-identical feathers.



The one in the back wasn't in a fighting stance.  He stood with his legs together, heels touching, back straight, one palm extended toward us.  He wore a mask that covered one eye and put an oversized lens in front of the other, with spikes radiating from it like the rays of a sun.  His costume was a very lightweight covering of layered and interlocking metal plates, more stylized than functional, but there was a coat-tail length of cloth extending behind the back, hanging to his knees.



I was careful in how I condensed the bugs around me.  I kept my team obscured as I pulled the bugs away from the four wards, leaving enough bugs on them that I could covertly follow their movements.  They hadn't been stung or bitten, and they didn't have a clear shot as the bugs moved away from them.  It meant, at least, that they'd get a chance to realize they weren't under attack.



The bugs filled the necessary pockets of my costume, then carpeted the exterior, including my mask.  They connected to the ends of my hair, and moved beneath it, giving it more volume and helping it come little alive, the `ends' moving in the absence of wind.  Where I had excess, they trailed several feet behind me like the hem of a royal gown.



``That's better,'' I said, augmenting my voice a touch.  It was.  I felt more centered, more secure and confident with the bugs close.  I'd just alarmed the people we'd be working with, but a small show of power would help ensure we got respect and cooperation.



``Your names and powers?'' Tattletale asked the Chicago Wards.  She gestured toward the door and we started walking briskly toward the exit.



``Tecton,'' said the power-armor wearer.  He had to raise his voice to be heard over his heavy footfalls and the rattle of furniture around him.  He indicated the boy to his right, then the girl, ``This is Wanton and Grace.  Our ranged attacker here is Raymancer.''



``Isn't Wonton a kind of noodle?'' Regent asked.



``And Raymancer?'' Imp asked.  ``They're really running out of stuff to call superheroes.''



``Play nice,'' Grue warned.



``Yeah,'' Tattletale said, ``A wonton is a kind of dumpling, not a noodle.  Get it right.''



``\emph{Wanton,}'' Tecton said, stressing the pronounciation, ``Is a breaker-stranger class cape.  He can turn into a localized telekinetic storm.  Raymancer is our long-range fighter.  The three of us are more close-combat types, but Raymancer manages to make it work.



``Grace is a martial artist.  She's got a power spread.  Faster perception of time, enhanced agility, and a striker-class enhancement for select body parts at a time; invulnerability to both powers and general harm, as well as increased effect on contact.\emph{``}



``And you?  Tinker?'' Grue asked.



``Tinker and thinker both.  Architecture and geology sense.  Armor lets me `ground' kinetic energy like you might do with electricity.  \emph{These} are piledriver gauntlets,'' he patted one gauntlet, ``For creating fissures, generating localized earthquakes and other controlled demolition.''



``Having tinkers against Noelle is probably our safest bet,'' Tattletale said.



``Because she won't copy their gear,'' I said.



Tattletale nodded.



``Good.  Thank you, by the way, for sharing,'' Grue spoke to the Wards.  Tecton nodded. Our groups had reached the door that led into the stairwell.  There were officers handing out armbands, and the elevator was in use, forcing us to wait as people got their armbands and hurried downstairs.



``You need our info?''



``No,'' Grace said.  Her voice was hard.  ``We know who you are.''



Imp cackled, ``We're famous!''



I hung back a second as one officer held an armband and my armor compartment out to me.  I gripped it, but he didn't let go.



He wanted to play it that way?



I let my bugs drift away from my armor to surround it.  He acted as if I'd set it on fire, letting go and backing away.  I handed it to Tattletale as we passed through the door to the stairs, then strapped on my armband.  I spoke into it, ``Skitter.''



How had things gone with Leviathan?  My username would appear.  I held my armband to Tattletale, and she pressed a button.



``No trackers hidden in your stuff,'' she said.  ``Want help putting this on?''



``Please.  When we're at the bottom.''



We were at the tail end of the group, and consequently we were the last ones out the door.  The dogs were already mostly grown, and we paused as Bitch increased Bentley's size to the point that we could ride him.



``We have too many people and not enough dogs,'' Grue commented.



``We'll drive,'' Tecton said.  ``Just need to requisition a van.''



``I'll ride,'' I said.  ``Rachel?''



She nodded.  She was up first, and she gave me a hand in getting up.  I had to fight coughing for a minute.



``Assault's going to try to screw us over, if we cross paths,'' Tattletale said.



``I suspected,'' I answered.



``And if this goes south, they \emph{will} come after us.  The bit Miss Militia said about Battery?  That loses its cachet when people start to feel like the people of this city would be better protected if they turned us in than if we were helping.  We're going to have to stay on top of this.  Turn around, I'll help strap on your armor.''



I nodded and turned around.  I moved my bugs out of the way as she fiddled with the straps, threading them through the appropriate areas.  I blinked a few times, looking towards the nearest light source to try to gauge if my vision was any better.  No improvement.  Short of a thorough check by an ophthalmologist, I wouldn't find out if I'd regain my sight, or how much I'd recover if I did.



Everything I'd been through, and I got the long-term injury as a \emph{civilian}.



Within two minutes, the Wards had pulled a containment van up beside us, with Tecton behind the wheel and Raymancer sitting in the passenger-side window, holding the headrest of the chair inside to help maintain his position.  The back popped open, and Imp, Regent, Tattletale and Grue climbed in.



\emph{Ballistic as our first stop.  Then Parian}.



I winced at the pain in my side as Bentley started running.  \emph{And maybe collect Atlas while we're in this area of town}.



Tattletale was right.  This situation being classified as a level-A situation instead of a class-S situation wasn't doing us any favors.  I just had to note how things were different from Leviathan's attack.  There were no air raid sirens.  People weren't being evacuated.



Helicopters flew overhead.  I could hear them, even if my bugs didn't reach that high.  I knew Miss Militia had assigned us capes, for the inevitable event of Noelle sniffing us out and coming after us.  I didn't sense them on the ground, so I could only assume they were in the air.



Was it better that people weren't being evacuated?  They weren't on the streets, in the line of fire if the psycho-Vistas or Noelle came after them.  It meant we didn't need to deal with unpowered clones.



But it also meant that there were that many more people here if things went south.



There was a potential kill order on our heads, and there were innumerable heroes in the city who had reason to throw us to the wolves, or to \emph{Noelle }if they thought the situation called for it.  The stakes were higher, and there was a lot more room to fail.  Noelle just needed one lucky maneuver to go from class-A to class-S threat in moments, and we weren't getting half the backup this situation deserved.



Not to mention that I was worn out.  Physically, emotionally, I felt like I'd been pushed to the limit, wrung out and then pushed to the limit all over again, and that was just dealing with Coil and rescuing Dinah in the past twenty-four hours.  If I got into the past few \emph{months}, or how the very way I thought had changed-



I felt a touch dizzy just thinking about it.



No.  It wasn't dizziness.  My surroundings really \emph{were} off kilter.  The buildings around us and ahead of us were stretching and shifting en-masse.



``Trouble!'' I informed Bitch.  I used my bugs to notify the others in the containment van: \emph{Vistas.}



I had to sweep my bugs over the area before I could find any of them.  One was perched on a rooftop, one block ahead.  She wasn't in costume.



It had been dumb of me to expect them to be in costume.  I hadn't even considered it, but Noelle wouldn't spit out anything but the people themselves.  The bugs noted the hardness of her face, more like a mask than flesh, her angular, almost artificial chin, and the thin hair on top of her head.



The others\ldots too many places to check\ldots I found another, three blocks over, making a beeline towards us.  Noelle had ordered them to space out, to catch us if we crossed her perimeter.



Bastard yelped to my left, skidded to a stop.  Rachel seemed to read something in his response, because she pulled Bentley to a hard left, veering straight into the van's path.



She was going to hit it?  I had to adjust my grip, lifting my leg out of the way before she could follow through and have Bentley bodycheck the vehicle.  I sensed Raymancer dropping from the window to his seat as the dog hit, only an inch away from serious injury.  The van turned and skidded to a stop, and I fell, rolling.



A block ahead of us, a building toppled.  I ducked my head low and covered it as dust and debris rolled past us as a thick cloud.  The building wouldn't have hit us, but the debris and dust might have left us incapacitated long enough for the Vistas to act.



We'd ground to a halt, and sure enough, the pseudo-Vista on the rooftop was slowly starting to work on the buildings around us, thinning walls and twisting supports.  She was spreading out the work and laying the groundwork for future collapses, I realized.  The second psycho-Vista, busy trying to close the distance by folding the space between us and her and stepping across the shortened distances, was raising the street between two buildings, creating a steep incline that even Bitch's dogs would struggle to climb, cutting off one avenue of retreat.



And I was aware of a third one.  The tall Vista Grue had described.  She'd stretched like taffy, her bones curving to the point that each was more a crescent than straight.  Narrow, so thin it felt like she'd break, with a face twisted into a perpetual, distorted scream, she was picking her way through the rubble of the fallen building.  Her power was twisting the largest pieces of rubble around her until they were wisps, chunks of concrete slowly corkscrewing in space until they were nothing more than dust.



Three of them.



And Noelle nowhere to be seen.  Not in my power's range of four-ish city blocks.  She'd be going for the others.  For Ballistic, or Parian.  These troops were only to slow us down, buy her time to make another move, find another set of powers.



Fuck me.  Noelle was employing the same basic tactics I did: sensing the opposition, strategically deploying the offensive troops, acting as the heavy hitter and problem solver in the center of the chaos her minions generated, working towards complementary or wholly different goals than the `swarm'.



Worse, she was better at it than I was.  She was faster, her senses reached further, and the individual at the center of \emph{her} army was a nightmarish force unto herself.



We couldn't afford to get caught fighting.  Not while Noelle hit our other allies.



Still flat on the ground, I choked back the next spell of coughs and touched the button on my armband, ``We need reinforcements, \emph{fast}.\emph{``}





