





``\emph{Help is on the way},'' Miss Militia's voice came over the armband.



``Three Vistas,'' I said.  ``And Noelle is probably north of our location, going after-''



``Skitter!''  Tattletale shouted, interrupting me, ``lose it!''



``What?''



``The armband!  Toss it!''



I pulled at the straps.  As I gathered bugs onto the armband to get a better sense of what I needed to do with the straps, I could tell that the entire thing was swelling, distorting.  I could hear the screen crack.



I pulled it free and threw it, simultaneously climbing to my feet and scrambling away.



``Grue!  Cover it!''  Tattletale shouted.  ``Use your power on anything that one breaks down!''



Grue threw out a stream of darkness, then dissolved the darkness that wasn't covering the area where the armband had been.  Without the ability to see, I had only my bugs' senses to go by, but I could track where he'd laid down the darkness by the way the air seemed thicker.



From Tattletale's words, I'd expected an explosion, but it simply twisted away into wisps of thick smoke.



``It's \emph{radioactive},'' Tattletale intoned.  ``Everything she's dissolving like that.''



``Unless I cover it?'' Grue asked.



``Unless you cover it.  Should cancel out the effects.  But you \emph{did} want me to let you know when I'm making an educated guess.  This is one of them.'' Tattletale said.  ``I hope I'm right.  We could win this fight and still wind up dying in a hospital bed a few years from now, because we got too close as that stuff dissolved.''



\emph{Oh shit.}



``Doesn't matter, does it?'' Regent said.  ``World's ending in a few years anyways.''



``Let's \emph{avoid} the extreme radiation poisoning,'' I said.  ``Regardless of whether the world's ending or not.''



The other Undersiders and the Chicago Wards were out of the van, and we were collectively backing away from the nega-Vistas.  More specifically, we were retreating from the one who was creating the radioactive dust.



The first one I'd noticed was still on the rooftop, spreading out her efforts, thinning walls and twisting supports.  Her progress was slow, but I was willing to bet that half of the city block would be collapsing onto us in a matter of minutes.  If not sooner.  If I had to guess, her power operated in a different manner than the original Vista's.  It affected a wider area, it was slower, and she didn't seem to be suffering for our presence.



The bugs that I was sending her way were having a hard time approaching.  They kept veering around so they flew clockwise around her instead of straight.  I had only a few bugs attacking her, but the same effect that I'd seen with her face had hardened her skin and there weren't many places left to attack.  Her mouth was little more than a lipless slit across the lower half of her face, firmly closed, and only the smallest bugs could get at her eyes.  She barely flinched at the bites and stings my swarm was delivering.



Meagre as my efforts were, they still should have left her blind, filling her eye sockets with ants and no-see-ums, but her power was still steadily working on the buildings around us.  Another peculiarity of her abilities?  The ability to sense the layout of whatever structures she was affecting?  Did that extend to sensing \emph{us}?



The second one had arrived, creating footholds and handholds to ascend the section of road she'd raised into a vertical wall, twelve feet high.  She was now perched on top, crouching.  In the time that it had taken me to lose the armband, she had started to work on cutting off our best avenue of retreat.  The road we'd traveled on to get here was raising behind us, bulging upward into a similar barrier.  As far as I could tell, her powers were most in line with the regular Vista, and she seemed to be reacting most to the bites and stings.  I wished that would make me feel more confident about these circumstances.



That left the freakishly tall one.  The Vista with limbs that zig-zagged, who was apparently turning matter into radioactive dust.  She'd climbed past the wreckage of the fallen building and now stood on solid ground again, facing us.



``We off the radioactive one first?'' Tecton suggested.



``No,'' I said.  I used my bugs to draw an arrow in the air.  ``Priority's the one on the roof, over there.''



``There's a third one?'' he asked.



Apparently he hadn't caught my message to Miss Militia.



``She's going to bring down more buildings if we don't take her fast,'' I said.



``Raymancer,'' Tecton ordered, ``handle it.''



Raymancer stood like he had before, feet together, one arm extended.  I didn't sense any energy blast or ray from his hand.  The Vista didn't act as though she'd been shot either.



``She bends \emph{light}!?''  Wanton asked.



``She's bending \emph{space},'' Tattletale said.  ``You won't get a straight shot.''



``Don't need one,'' Raymancer said.  His second shot left a shallow crater in the Vista's chest.  She sprawled onto the roof, hands pressed to the injury.



The thinning of the walls didn't stop.



``How the fuck does that work?'' Regent asked.  ``The laser didn't even-''



``She's still alive!'' I called out, interrupting him.  There was a small explosion as  Raymancer directed a shot at the Radioactive Vista and missed.  I could sense how the barrier behind us abruptly stopped growing and how the space to one side of her warped to let her evade more easily.



``Vista to our three o'clock is assisting her!'' I said.



``Grace!'' Tecton shouted.  ``Leaving rooftop to you!  Launch!''



Grace leaped toward him, onto the back of one outstretched hand.  She had no trouble maintaining her balance as she placed the other foot on the back of his other gauntlet.



She bent her knees, and extended them to jump in the same instant the piledriver attachments on the gauntlets extended with explosive force.



Most of the bugs I'd placed on her were torn free by the force of the wind ripping past her, as she turned into a human projectile.  She had to have used her selective invincibility to augment her feet and legs so they weren't annihilated by the piledrivers, and she would be using her enhanced agility to ensure she stuck the landing.



Except the landing wasn't going to happen as planned.  If I'd understood what they'd planned, I would have warned her.  Her trajectory shifted as she ran into the rooftop-Vista's power.  Grace fell short of reaching the rooftop.  \emph{Very} short.  She hit the ground with both feet together, arms spread, and left a shallow crater around her impact site, a half-block away from the building.  Grace was running toward her target a heartbeat later, unhurt.



Some of the flying capes that had been assigned to watch over us were targeting the Vista on the rooftop, and I saw that as excuse enough to focus on other, more immediate problems.



Rachel and her dogs went for the Vista to our right, with Regent doing what he could to hamper their target's movement, forcing her to use her \emph{power} to maintain the distance from the beasts.



Which left the rest of us to face off against the radioactive one.



``One on the rooftop's occupied,'' I said.  ``\emph{Now} we can fight her.''



She extended her hand toward us, and the ground between us and her bulged, as though a cartoon mole had crawled beneath the pavement.  Raymancer fired at her, clearly hoping to distract her, but each shot missed by a fair margin.



My bugs were covering every inch of her skin, and I had them biting and tearing at her flesh.  Her skin was hard, gnarled, and calloused, but I did the damage where I could at the elbows, knees and neck, drawing blood.  I tried to tell myself that she was a monster, a mockery of a real person, and she was too dangerous to be allowed to live.  With that kind of unhinged mental state, and her ability to irradiate people\ldots  I grit my teeth.  No choice.



Grue finished covering the bulging ground with darkness.  Tall-Vista didn't react.  Her hand was still pointed at us.



``It's a feint!''  Tattletale shouted.  She spun around.  ``There!''



My swarm moved in the direction Tattletale was looking.  I found the bulge, a basketball-sized blister on the side of the containment van, felt it erupting a mere foot from Raymancer's head a half-second before Grue's darkness covered it.



Too late.  Raymancer stumbled, coughing.



Grue turned and extended a hand toward the tall Vista.  With my swarm spread out around her, I could sense miniscule explosions appearing all around her, see the flashes of light with the bugs' distorted vision.  The individual detonations weren't much larger than golf balls, and even the direct impacts weren't enough to kill my larger bugs.



``How the fuck do you use Raymancer's power?''  Grue asked.



``You copy powers?''  Wanton asked.



``Thought you guys read up on us,'' Tattletale quipped.  ``Grue, focus the beams with the lenses.  The beam appears from the center, so line them up to refine the beam into something more effective.''



``In case you haven't noticed, I've only got the \emph{one} lens there.''



\emph{Lenses?  }My bugs weren't sensing anything.



Wanton was closing the distance, now that the other Vista was distracted trying to avoid Bentley and Bastard, still hobbled by Regent's power.  As he got halfway to her, the ground around her began to distort and twist into curls.  Wanton disintegrated as he entered the area.



For a heartbeat, I thought she'd used her power on him.  When the debris, dust and chunks of building began stirring and orbiting a central point that continued his general trajectory, I realized it was \emph{his} power.



Wanton didn't hesitate as radioactive dust exploded around and inside his new body.  If anything, it proved an advantage, as the dust provided more material to work with and the damage to the street let him pull up chunks of pavement.  He closed the distance to our opponent and began thrashing her.  One of her arms snapped and dangled as one large chunk struck her.



Grue's attacks weren't terribly effective.  There were only half the number of explosions, but they \emph{were} sufficient to kill bugs if they happened to hit one.  He abandoned Raymancer's power and cast out his darkness toward the Vista.  A moment later, the ground under her feet was contorting, and dust was rising around her.



To our right, Rachel and Bastard were closing in on the Vista.  Her foot was contorted by Regent's power, and her neck was craning at awkward angles, making it harder for her to focus on them and use her own abilities.



She backed away, raised her one good hand in their direction, and promptly bumped into Imp.  Before the pseudo-Vista could react, she had a taser pressed to her neck.



Rachel closed the distance, Bentley loping forward.  My bugs caught her voice.  An order, not too hard to make out.  Not with the context.



``Kill,'' Rachel said, her voice quiet.  The bulldog picked up the Vista in his jaws and bit down until an audible series of cracks marked the breaking of a dozen major bones.  He shook her like a rag doll, no doubt snapping her neck and aggravating every injury he'd just inflicted.  The girl was dead in an instant.



Rachel's ordered him to drop the body, ordered Bastard to back away from the carcass, and then took hold of Bastard's chain.  She started to wheel Bentley around to rejoin us, but I was already drawing arrows in the air.  Wanton wasn't at risk from the radiation in his new form, apparently, but Rachel and her dogs were.  There was nothing saying that any radiation wouldn't be able to penetrate the monstrous flesh and hit the dog nestled in the core.



Kicking Bentley into an all-out run, she led Bastard in an all-out toward the one on the rooftop.  No hesitation.  No apparent remorse.



Rachel and I had grown closer, to the point of maybe being friends on top of being teammates.  Whatever rifts had formed between us were largely mended, and she trusted me as a leader.  With all that in mind, it was sometimes hard to remember that she was still \emph{Rachel} at the core of it.  If her psychological wiring didn't give her any real empathy for her fellow human beings, it wasn't about to give her any for human-\emph{esque} beings.



Tecton slammed one gauntlet into the ground, creating a crack that rushed toward the taller Vista.  It exploded in a geyser of debris and dust as it reached her.  She staggered, then staggered again as Grue landed a shot with Raymancer's power.  She tried to raise one hand to defend herself, but the thin, curved bone of her upper arm had been shattered.  Her broken arm dangled in front of her.



With the topographical map my swarm provided, I noted the presence of thick veins standing out on her arm, where the weight of the dangling limb pulled the skin tight against the shattered bone.  I barely thought about it, sending my bugs to the area, biting deep into the largest one, working together so that one hornet might pull one way, a beetle pulling another, to better rend the flesh or positioning it for a stronger bug to bite into.



She jerked in reaction, and blood began flowing.  Beads of it at first, but the skin was pulled tight and the bugs were relentless.  It virtually tore between the combination of damage and strain.  A small river of blood flowed, intermittently spurting.



That would be an \emph{artery}, not a vein.  \emph{Fuck me}.  I tried to suppress the quiet horror that took hold of me as my bugs tracked the blood pouring down her arm, trickling off her fingertips in individual streams.



Still fighting to avoid being brained by Wanton's telekinetic storm, the tall Vista let out a drawn out half-moan, half-scream, equal parts despair and anger.  It didn't sound exactly normal, but that didn't surprise me.  What made my blood run cold was that she\emph{ almost} sounded like a young girl might.  A little too close to reality for comfort.



She went all-out with her power, aimless, directionless.  Street signs, mailboxes, piles of debris, walls and sections of road began twisting and bulging.  Grue laid down a blanket of darkness all around us, aiming to dampen the spread of the radioactive particles.  I wasn't sure how that worked, but \emph{Tattletale} thought it did, and I wasn't about to complain.  I'd settle for a white lie if it meant we were able to stay focused on fighting, rather than the cancer we'd have five years from now.



It took ten seconds before the Vista collapsed.  Only ten seconds to bleed out to the point of unconsciousness.  The blood continued pumping free, and nobody leaped forward to staunch the flow.



I sensed some of the faster capes from Miss Militia's group making their arrival on the scene.



The wound the rooftop-Vista had sustained from Raymancer was shallow, the majority of it consisting of surface damage to her artificially smooth, thick skin and to her ribs.  I'd only peripherally been aware I was doing it, but my bugs had seized on the opportunity to dig in and attack the more vulnerable flesh of the open wound. She barely seemed to care, focusing her efforts on diverting incoming fire and trying to distort the rooftop to force Grace to fall off.  That changed when several bugs found a hole leading into the empty space surrounding her lungs.



In that same moment, the Vista started trying to claw the bugs out of the shallow cavity.  The distraction afforded one of the heroes a chance to catch her in the head with a gobbet of foam.  A smaller containment foam blaster?



Flying capes closed the distance and settled around her.  There was a brief dialogue that I couldn't make out with the unfamiliar voices.  Someone said something about foam, there were a few words of argument from a pair, and one pressed a finger to their armband, saying something about a captive.



It was Miss Militia who responded through the armband.  She gave a curt order, and several capes turned away.  One of the capes who hadn't took aim and shot the fallen girl between the eyes.



The fight was over.  The heroes were already moving north in pursuit of Noelle.  I signaled for Rachel to return.



That moan-scream the tall Vista had made was still ringing in my ears.  It had been way too human for my tastes.



There was no doubt she'd been going all out.  Raymancer was on his knees, supported by Tecton.  He'd taken a hit of the dust straight to the face.  If Tattletale was right\ldots he'd just taken a lethal dose of radiation.  The clone hadn't even flinched in delivering the attack.



I'd had fights like this.  Dealing with the Nine had been much the same, had demanded we hold nothing back, had involved enemies who didn't hesitate.  The difference was that the Nine had demanded it because anything less wouldn't cut it.  Fighting these clones, they were \emph{vulnerable}.  They only defended themselves so they could keep causing damage.  When I tried to hurt them, they \emph{got hurt}.  It sounded so lame when I framed it like that, but\ldots it shook me.



Even knowing they were deranged, that Tattletale had confirmed they weren't really \emph{people,} I couldn't ignore how brutal we'd been.  My actions.  The clones weren't innocent, but they were \emph{innocents}.  If that made any sense.



And I knew I'd have to do it all over again, the next time we ran into a clone.



Tattletale touched Grue's arm, and he banished the darkness around us.



``I'm going to die,'' Raymancer said, his voice barely above a whisper.



``There's a good chance, yeah,'' Tattletale said.



``Hey,'' Tecton said, ``Don't be a bitch.''



She didn't respond.  Instead, she touched her armband, ``Raymancer down.  He needs immediate medical attention for acute radiation poisoning.  Quarantine this location, you'll want stuff for radioactive decontamination, mobile showers if you've got them.  Oh, and Skitter's armband is out of commisison, we need a replacement before someone mistakes her for a clone.''



``\emph{Keep close to her, Tattletale,}''  Miss Militia said.  ``\emph{And we'll deliver one shortly.  Quarantine, civilian evacuation and decontamination are en route.}''



``We're moving on to check on Ballistic.  Your man can meet us there.''



``If they can track us with the armband, they can follow us to his headquarters,'' Grue commented.



``He can move bases,'' I said, ``Finding him fast is a bigger priority.''



``He won't like that,'' Grue said.  ``Going from a well set-up base of operations to some place improvised?''



``He didn't want to come today, he deals with the fallout,'' I said.  I waved as Rachel approached.  She was still holding Bastard's chain.  ``Let's go.''



``Tecton?'' Tattletale asked.



``I\ldots I can't leave Raymancer here,'' Tecton said.



``Wanton can watch him,'' she said.



I looked at Wanton.  He was still in his telekinetic form.  To my swarm sense, he gave me the impression of a miniature galaxy, with dust and various objects orbiting a central point.  When he moved, the outer edges took longer to catch up than the bits closer to the center, almost like a jellyfish in water.



``Hey, W,'' Tecton said.  ``Fight's over.''



``He can't change back,'' Tattletale said.  ``If he does, that dust he drew into his t.k. body is going to settle, and then he'll be in the same shape Raymancer is.  Maybe everyone in his vicinity will.''



``But-''



``But they can stick him in a decontamination shower,'' Tattletale said.  ``Just needs to hold himself together long enough for that to happen.  Not to worry.  Fifteen minute decontamination and he's clean.''



``Longest he's ever held that form was \emph{twelve} minutes.''



``Then he'll need to hold together for longer.  But we've got to get ahead of Noelle before the next trap is set up.  We need you to come with us.''



``You want me to leave my team,'' Tecton said.



``We could run into more Vistas.  She warps space, distorts architecture.  If the next batch is organized enough to cut off \emph{all} avenues of retreat while keeping their distance, or drop more buildings on us, we'd need you to help.  Rachel's dogs aren't going to be able to get us free if Vista buries us, or if she traps us under some bubble of stretched building.''



``Go, T,'' Raymancer said.



``But you-''



``I'll get looked after, and I'll give Wanton he encouragement he needs to break his old record.  Get Grace and \emph{go}.''



``You heard the man,'' Tattletale said.  ``You want to drive?''



``You go ahead,'' Tecton said.  ``Driving with the suit is a hassle.''



``All the better,'' Tattletale said, cheery.



Tecton didn't reply as he got into the van.  I climbed onto Bentley's back.



The van had to take a detour, given the three sections of road that had been raised as barriers and the one fallen building.  Bentley wasn't so disadvantaged.  We crossed the ruins of the toppled building.



I could smell the thick, metallic scent of blood in the same moments that his hot breath wafted past me.



I wondered if I should be in the van.  I could communicate with Tattletale and Grue if I was, and it would mean I wasn't experiencing an agonizing pain in my side every time he set his feet down with too much force or leaped an obstacle.



That said, I wasn't sure I wanted to turn Rachel away if she was being friendly.



The van stopped to pick up Grace.  They traveled down a different street, moving parallel to Rachel and I.



``\ldotsso fast?'' Tecton asked.  I couldn't make it all out.



I caught the tail end of Tattletale's reply: ``\ldots a trap.''



I drew out letters on the dashboard with my bugs: `Trouble?'



She shook her head.  I didn't catch what she said.  She repeated herself.  ``\ldotsventative measure.''



\emph{Preventative measure}.  She was picking up the speed so any other enemies that were lying in wait would have less time to spring any surprises on us.  I scattered the bugs, left a brief `ok' and then removed those.  I caught Tecton saying something, but couldn't make it out.  His mask didn't help.



I redoubled my efforts to check our surroundings and find any possible clones of Vista, Uber, Leet or Circus.



We caught up to a group of the faster-moving heroes who'd flown ahead.  They were dispatching another Vista.  She was shorter, thicker in the arms and legs, with a neck as thick around as her head was.  The space around her was twisted into jagged shapes, with some raised into points.  Two of the capes had been injured but were still fighting.



We rode past, and the van with the others gave chase.



The flying capes weren't moving with purpose.  They were roving the area, going west-to-east and back again as they moved in a general northerly direction.



We were nearly at Ballistic's base when a digitized voice sounded over the armband.  Not Miss Militia.  Dragon's A.I.   ``\emph{We have a sighting.  All cooperating capes are ordered to stand down.  Remain at your present coordinates until further notice.}''



\emph{Stand down?  }I tapped Rachel on the shoulder, and she pulled Bentley to a stop.



The armband buzzed again, but it was Miss Militia's voice this time.  ``\emph{Eidolon has found our primary target.  He has requested that all capes in the area remain in position}.''



I caught Tattletale pressing the button on her armband.  She asked, ``Why?''



Whatever program was managing communications, it didn't see fit to convey Tattletale's message.



The van caught up to us.  Tattletale rolled her window down, and opened the back.  The others climbed out to join the conversation.  Grace folded her arms and hung back.



``What's going on?''  I asked.



``Don't know,'' Tattletale said.  ``But if Eidolon is fighting Noelle\ldots''



Regent finished her sentence for her, ``We might not have to worry about the end of the world happening in two years.''



``Why is Miss Militia letting this slide?'' I asked.  ``She has to know the risk.  \emph{Everyone} has to know the risk.''



``She's letting this slide because Eidolon outranks her and she has no choice,'' Tattletale said.  ``And \emph{he's} doing this because he's got an agenda.''



``An agenda?'' Grace asked.



``Yeah.''



``He's the top hero in the Protectorate.  His \emph{agenda} is doing the right thing.  Is this what you guys do?  You analyze the situation until you've twisted it into a scenario where you just \emph{have} to do something?''



``Yeah,'' Regent said.  ``We're really good at it, too.''



``Ha ha,'' Grace said, without any humor.



``Look,'' I said.  ``Fine.  You guys are helping us, so you get a say.  If you guys are willing to hear me out and you decide that there's no merit to what I'm saying, we can go along with what you want to do.''



``Hear you out?''



``Yeah.  Look, you can't deny that putting one of the most powerful people in the world in close quarters with someone who could turn \emph{Vista} into those things is a fucking bad idea.''



``Sure I can.''



``Play nice, Grace,'' Tecton said.



``No, I'm going to make my arguments.  He's not \emph{stupid}.  He knows what he can do, and he's heard what she can do.  You don't get to be a member of the \emph{Triumvirate} if you're an idiot.''



``He's desperate,'' Tattletale said,  ``He's losing his powers.  He knows putting himself in dangerous situations makes his power stronger, like how one of my teammates gets a little stronger when outraged, and another gets a little stronger when feeling protective.  Fighting Noelle is nearly as dangerous as fighting Endbringers.''



\emph{Endbringers}.  When Leviathan had attacked, it had been destruction layered on top of more destruction.  Noelle was being pretty damn subtle for someone who could tear vault doors apart and generate an army of superpowered soldiers.



Even in terms of the overall impact of her assault, as far as I knew, it had been limited to one fallen building, two injured capes and one in critical condition.  It felt like too little.



Then again, the sun wasn't up.  Dinah had said Noelle wouldn't do any \emph{real} damage until dawn.  Would things get worse?



``How long until sunrise?'' I asked, cutting Grace off just as she started to voice a response.



``Nine minutes,'' Tattletale answered.



``Dinah said the situation doesn't start getting \emph{really} bad until dawn\ldots'' I trailed off.



``You think this is why the situation goes south,'' Grue said.



``It's a possibility.''



Tattletale pressed the button on her armband.  ``This is \emph{really} bad timing on Eidolon's part, M.M..  Shit's due to go down at sunrise.  Can you call him off?  Remind him?''



There was no indication the message went through.



``Fucking computer,'' she said.  ``Let's go.''



``No,'' Grace said.  ``You said it was our call.  I don't buy the argument.  We stay put.''



``Tecton?'' I asked.



He was still in the passenger seat.  ``I don't know.  Are \emph{you} willing to disobey the order and have Miss Militia okay a kill order on you?''



``\emph{Try} to okay a kill order on us,'' Imp said.



``Oh, well then,'' Tecton said.  ``\emph{That's} not a problem.''



I thought about the possible scenarios that could unfold.  Deranged Vistas had been brutal enough.  Deranged mutant \emph{Eidolons}?



``Yeah,'' I said.  ``If it comes down to it, I'm willing.''



``Be it on your heads,'' Tecton said.



``Get in if you're coming,'' Tattletale said.  ``Get out if you're not.''



Tecton hesitated, but he stayed in his seat.



``Tecton?'' Grace asked.



``They believe it enough to go this far.  They've either got an unhealthy amount of conviction or they're insane-''



``Or both,'' Imp said.



``Or both.  If it's conviction, I can accept that they \emph{might} know what they're doing.  The same argument you made about Eidolon being an upper echelon member of the Protectorate applies to them.  They didn't get here by being terrible at what they do.''



``They \emph{did} get to the point where they're about to get kill orders put out on them, and you stand to get in trouble with the Wards.''



``What's the worst they could do?  As a tinker, I'm a protected species.  Not like they're going to \emph{fire} me.  If these guys are \emph{right}, they might need our help.  If they're wrong, maybe I get in a bit of trouble.  I'm willing to take that bet.''



``And if they're trying something?  Or if they \emph{are} insane?''



``Then it's better I'm along for the ride, isn't it?''



Grace didn't respond.  Instead, she turned around and walked away.



When she reached the back of the truck, she hopped in.  ``You fucking \emph{owe} me, Tec.''



She slammed the one door closed, as if to punctuate her irritation with the situation, leaving the other open for my teammates.



Tattletale dropped her armband out the driver's side window.  The rest of the Undersiders discarded theirs.  There was a pause before Tecton and Grace followed suit, throwing theirs free of the van.



That done, Tattletale put the van in gear.   It was already starting to move by the time Imp and Regent had climbed in and slammed the doors behind them.



With Tattletale's ability to identify Eidolon's general location and my ability to narrow the result down with my bugs, it only took a few minutes to find them.  The issue was that we only had a few minutes to begin with.



Eidolon was in the air, flying a safe distance above Noelle.  And Noelle\ldots



I couldn't get a read on Noelle.  My bugs disappeared into her as they made contact, their signal distorting and cutting off.  It left me with a hazy picture.  She was big.  African elephant big.  I didn't get much more than that.



They were \emph{talking}.



Eidolon had his hands folded into his sleeves, like an ancient sensei, legs dangling, his costume billowing around him.  His voice was calm, quiet, in stark contrast to the hot breath that billowed around Noelle as she panted with no less than five mouths.  Four of the mouths were considerably larger than the one owned by the rough human shape on top.



I only caught two words as he spoke to her.  Coil was one.  Cauldron was another.





