





``He's talking to her about Cauldron,'' I said.  ``And Coil.''  I'd signalled the others to exit the van, and we were gathered around Bentley and Bastard.



``Cauldron?''  Tecton asked.



``Cauldron worked out a formula that could give people powers, and the capes with monstrous features are the failed results,'' I said.



``The Case 53s,'' Grace said.



Tattletale nodded.



I raised my finger to my lips.  To where my lips were behind my mask, really.  I wound up sliding my hands beneath the sides of my mask to plug my ears.  I'd hoped to shut out other sounds and allow myself to focus.  It wasn't too helpful.



Tattletale murmured something to Grue, and he surrounded us with darkness, leaving a clearing so we could communicate.  It took me a second to realize why.  Were he and Tattletale hoping to mask us from Noelle's other senses?



Rachel's dogs could smell through the darkness, couldn't they?  It wouldn't stop Noelle if she really was \emph{smelling} us.



``\ldots{}saying he knew them\ldots'' Noelle said.  \emph{Is that a question}?  I was having trouble discerning tone.



``\ldots{}m saying exactly that, Noelle,'' Eidolon replied.  ``\ldots \ldots very beginning.  Coil involved \ldots \ldots people who made you like this.''



``I don't believe\ldots No.''



``Eidolon just said \emph{Coil} was involved with Cauldron.  And that \emph{Cauldron} is responsible for Noelle,'' I informed the others.



``Another of Coil's schemes?'' Grue asked.  ``But why would he make Noelle?  What does that serve, really?''



``He didn't make her,'' Tattletale said.  ``But the rest is very possible.''



I'd spoken because I was worried I wouldn't get a chance later, between fatigue affecting my memory and the possibility of an imminent fight.  I'd missed some of what Eidolon said in the process.  ``\ldots{}help you.''



``I've had too many\ldots'' she said one word that was too complicated for me to make out.  ``\ldots{}of help.  Can't get my hopes \ldots \ldots''



I was disappointed in how limited these senses of mine were.  They were \emph{useful}, but the tactile nature of my swarm-sense left me blind as to people's changes in expression, and listening in like this, I could only catch the individual speech sounds, working out how they fit together into words while trying not to fall too far behind.  I wished I'd devoted more time to trying to figure out my swarm-sight and swarm-hearing.



Eidolon said something, and I couldn't decipher the word.  He paused, so I grasped that there was some meaning there.  Ended with -tive or -shiv\ldots prerogative?



Alternative.  It connected just as he started speaking again.  ``Do you want to die\ldots''



``Yes,'' Noelle's answer was clear.



``I'm \ldots{}red to die too,'' Eidolon said.  There'd been another longer word in the middle there that I couldn't afford to stop and work out.  ``My danger sense tells me you \ldots alone.''



``No,'' Noelle said.  She bumped into more of my bugs as she shifted position, moving one large leg that was likely so thick around that three people together couldn't have reached around it with their hands meeting.  The bugs disappeared from my power's senses.



``Why don't you \ldots us\ldots'' Eidolon said.  Introduce.  It only made sense as a question:  \emph{Why don't you introduce us?}



``Show my hand\ldots''



``Why not\ldots'' Eidolon said, and I missed the tail end of it.  Another question?  I was starting to get a headache, trying to process all this.



Something peeled away from Noelle's side, and when it bumped into my bugs, they \emph{weren't} absorbed.  The stature, the length of the hair\ldots another Vista.



I thought maybe Noelle had produced another clone, but others started to emerge from the surrounding architecture, peeling away from nearby walls as if they'd been \emph{inside} the surfaces.



And they weren't all Vistas.  I noted the presence of what had to be a Circus, disproportionate and thin, with a hunched back, using her knuckles to walk.  There was another Vista, two large figures who might have been \"{U}bers, and on the second floor of the building behind Eidolon there was a narrow young man, shirtless, with a gun bigger than he was.  Leet.



``\ldots{}not expect you to \ldots a trap,'' Eidolon said.  He hadn't budged, and as far as I could tell, his tone of voice hadn't changed.



Noelle didn't reply.  From her vantage point, she had to be able to see through the open, glass-less window behind Eidolon, see the Leet silently setting up the gun.



``Trouble,'' I said.



Grue banished the darkness.  ``Trouble?''



``She's ambushing him.  There's a Leet with a gun inside the building behind him.  Tinker made, has to be.''



``Eidolon knows what he's doing,'' Grace said.



``And if he doesn't?'' Tattletale asked.  ``If that gun just happens to be able to punch through any invincibility or whatever it is he's given himself?''



``He's better than that,'' she said.  ``He's \emph{Eidolon}.''



``He's human,'' I said.  ``Humans make mistakes.''



``He's Eidolon,'' she repeated.



``I'm with Grace on this one,'' Tecton said.  ``Too dangerous to go.  She has a vendetta against you guys.  It's not worth the risk that you'd throw his plan into disarray.''



``Then why are we here?'' I asked.



``If things fall apart,'' he said, ``We can act \emph{then}.  Eidolon's powers are weakest just after he changes them.  If she creates a clone of him, the clone will be picking the powers for the first time.  There'll be a window of opportunity where we can take them out.''



``Assuming we can get close enough,'' Grue said.



``And there's a good half-dozen capes around her,'' I said.  ``One Circus, one Vista that can apparently hide people in two-dimensional space, two \"{U}bers and the Leet with the gun.''



``We compromise,'' Tattletale said.  ``Skitter, draw arrows on the ground, discreet but easily readable.  Point the way to the Leet, okay?  The rest of us hang back, and we wait to make sure we can get Eidolon out of a bad situation if one crops up.''



I started to draw the arrows.  I was going to ask why, but I realized I was missing what Eidolon and Noelle were saying.



``\ldots{}think you can win\ldots'' Eidolon said.



``I hope I don't,'' Noelle replied.



``\ldots \ldots want to die, why fight\ldots''



``Can't think straight.  My \ldots wiring is all screwed up.  Won't \emph{let} me give up.  Too angry, too \ldots{}less.''  \emph{Ruthless? Restless?}



Leet was still setting up.  He'd had to find a point where there was an open door, just so he had enough space behind him that the weapon could be positioned horizontally.  The design was crude, hodgepodge.  It resembled Squealer's work, just going by what I was interpreting with my swarm-sense.  That meant there was an excess of openings and gaps.  The part that burned hottest had to be the power source.  It was at the very back of the gun, at the point furthest from the mutant Leet.



I sneaked cockroaches in through the gaps in the weapon's exterior and started them chewing through the wiring.



``\ldots \ldots you so sure that you'll be any calmer when they're dead?'' Eidolon asked.



``I'm not.  \ldots I'm \emph{angry}, and it's like the \ldots have been taken off my emotions.  My anger, my \ldots{}tion, the pain, the hate, \ldots so much deeper.  \ldots it's not mine.  Not my emotion, so I can still think \ldots .''



``They're both stalling,'' I said.



``Eidolon's picked the powers he thinks will win the fight,'' Tattletale said, ``And is waiting for them to get up to full strength.  Noelle's waiting for her evil-Leet to shoot.''



``I'm trying to sabotage the gun,'' I said.  ``But it looks like he'll be ready to shoot any second now.''



Tecton and Grace simultaneously looked at one another, but they didn't speak.  What was that about?  Was their faith in Eidolon faltering as I described the situation, or was it more about \emph{me}?



``Less than a minute,'' Tattletale said.



``I'm pretty sure we don't have that long,'' I retorted.



The words had only just left my mouth when Leet dropped to a position at the side of the gun, putting one eye to the scope.  The entire weapon shifted on the tripod mount as he aimed.



Eidolon's head turned slightly, as if he were looking at Leet out of the corner of one eye.



Leet pulled the trigger.



``There we go,'' Eidolon said.  The gun wasn't firing.  He pulled the trigger again, and an arc of electricity ripped out from a space by the power supply, toasting half of the bugs I'd positioned on Leet and sending him sprawling to the ground.  He was back on his feet seconds later, tearing one panel away to get at the sparking power supply.  Tougher than a normal person.



``Attack!'' Noelle screamed.



Her minions started to move on Eidolon, but it was \emph{Eidolon} who acted on the command.  He swept one arm out in front of him, as though he were brushing a curtain aside or waving away some bugs.  There was a crash we could \emph{feel} where we were huddled together, making the ground shake.



In that very instant, Eidolon had killed the vast majority of the bugs I'd placed in the area.  It took me a second to process what he'd done.



The bugs that were still alive were unable to move, pressed hard against the ground to the point that they were sinking into the soft earth.  Even the more durable cockroaches had died where the ground wasn't soft enough for them to be pushed down into it.



Through the few surviving bugs, I could get a sense of what was happening.  Tufts of weeds that had stuck up between slats in the pavement now laid flat against the ground, as though they'd been starched and ironed in place.



The effect only lasted a few seconds.  I tentatively moved more bugs into the area to do an inspection, found the air both dense and strangely warm.  The ground had shifted, and both the pavement and the concrete panels of the sidewalk had cracked.  Chunks of rubble had been pulverized, piles of debris pancaked against the ground.  Plywood, siding and wood paneling had been torn from the faces of nearby buildings, rendered into unrecognizable fragments of wood and plastic.  Each fragment had been mashed flat or shoved into cracks and crevices.



The \"{U}bers and the Circus were dead, pulverized against the ground with their limbs broken in multiple places, their chest cavities and skulls cracked like eggs.  The Vista was nowhere to be seen.



Eidolon hadn't moved, and a tentative search told me that Noelle was still standing.  My swarm noted the presence of blood dripping to the ground beneath her massive body.



Eidolon said something, but I didn't have enough bugs in the area to hear him.



``He just crushed \emph{everything} around her,'' I said.  ``Almost as if he dropped a house-sized, invisible anvil around her.''



``Around Imp?''  Tattletale asked, gripping my arm.



``Around Noelle,'' I said.  ``What do you mean, Imp?''



``The building where Leet was--'' Tattletale started, grabbing my arm, ``Did he hit it?''



``No.''



``Turn the arrows around!  Give every warning you can!  We just sent Imp in there to deal with Leet!''



I did as she asked, using every bug I could to draw warnings, turning the arrows to point to a retreat.



``\emph{Damn it!}'' Grue said, ``Why did we send her in there!?  We need to get in there, in case anyone--''



``\emph{Stay},'' Tecton warned, ``Evacuate your teammate, but don't get in Eidolon's way.''



There was another crash.  Once again, the vast majority of my bugs in Noelle's vicinity disappeared.  Only a small few who were lucky enough to be in the right place and tough enough to endure the pressure survived.  The bugs who had been flying above Noelle sank into her flesh.



Through them, I could sense her advancing, moving one massive leg forward, relaxing and letting the pressure Eidolon was generating slam the limb into pavement with enough force to crack it.  Then she moved another leg forward.



Eidolon floated higher, maintaining the same relative distance between himself and her.



She dropped lower to the ground, as though she were succumbing to the pressure, then leaped in the same instant the last of the bugs who'd sunken into her flesh were absorbed.  I couldn't follow what happened next.



There was another crash, another earth-shaking rumble, and even the bugs who'd survived before were obliterated, leaving me utterly blind.  I moved a few bugs closer, to gauge if the effect was still active, and they died as though they'd moved beneath a falling hammer, going splat against the ground at the effect's edge.



Behind Eidolon, Leet had finished fixing the gun, helped by the fact that the electricity had killed my saboteur-cockroaches.  In the same instant he moved to take position by the trigger, Eidolon turned around, raising one hand in his direction.



And Imp was there.  She drew her knife across the psycho-Leet's throat.  Eidolon froze as Leet staggered and slumped against the windowsill, blood pouring from the open wound.



I felt a momentary confusion.  Leet was \emph{dead}?  Eidolon seemed to be reeling as well, but he recovered faster.  He wheeled around to strike out with the effect again.



``Leet's dead,'' I said.



``How?'' Tattletale asked.



``Throat slit.''



``Imp.  She's not listening to instructions.  Did Eidolon attack Leet?''



I shook my head.



She released my upper arm from the death grip she'd been maintaining since Eidolon had attacked.



It wasn't like her to get that upset.  She usually had more information to work with, so she had a better idea of what was going on, but that couldn't account for her full reaction.  I wished I could read her expression.



Leet slumped almost entirely out the window.  In a dying gesture, he feebly reached out for the end of the gun, gripping the barrel.  When he fell from the window, he kept hold of the gun.



The tripod skidded, and momentum coupled with Leet's weight pulled the gun after him.



Eidolon glanced over one shoulder at the body falling from the second floor window, then soared straight for the sky.



I was already sliding from Bentley's back, heading toward the ongoing battle.  The movements, Eidolon's reaction, everything spoke to something deliberate, something devastating on Leet's part.



The weapon's power supply detonated on contact with the ground.  I didn't have many bugs in the area to track it, only experienced a momentary sensation from the bugs in the area, much like I sensed when they were burned or electrocuted.  When the sensation disappeared, they were gone, dead.



I \emph{could} see the actual explosion, a flare of white that I could most definitely make out with bug eyesight and with my own damaged eyes, a glow that rose above the buildings around us.



``\emph{No},'' Grue said, just behind me.  The both of us had stopped in our tracks in the wake of the explosion.



My bugs flooded into the area, to give me a better sense of what was happening.  I caught Noelle stampeding toward a tall building. She had been in the blast radius, and she hadn't slowed down.  I \emph{hoped} she hadn't slowed down, because she was damn fast.



She wasn't in Leviathan's speed class, but she was moving at the sort of speed I might expect from a car on the highway.  Maybe the comparison wasn't so apt, because she was a living thing.  Like a predator, she shifted from a standstill to eighty miles an hour in a heartbeat.  She was more like a rhino than a jungle cat, though, and she was ungainly.  My bugs could track the vibrations of her footfalls better than they could trace her outline, and I could sense how her movements weren't synchronized.  There was no pattern to how her legs moved; rather, it was as if each leg had a mind of its own.



Still, the sheer \emph{power} of her movement carried her forward, while having six or more legs meant she always had several feet on the ground for balance.



She reached the base of the tallest skyscraper in the area and scaled it just as fast as she'd moved over ground.  Chunks of concrete were pulled and clawed away as each of her feet found or made footholds.  The debris fell in her wake, but her movement was steady and unfaltering.



Eidolon turned her way, laid down that same \emph{pressure }he'd applied earlier, tearing a full  third of the building to the ground.  A large part of the upper floors cast straight down, torn free of the building's housing.  The debris moved straight down with such force that it punched through as many as five or six of the floors below.  Noelle was already moving out of the way as the attack landed, circling around to the other side of the building, still climbing.



She reached the top before the dust from Eidolon's destruction rolled past us.  I held my breath.  I couldn't afford another coughing fit.



We made our way to the spot where their fight had started.  Where Eidolon's power had struck, the pavement had depressed until it was a good two feet lower than where we were standing.



``Imp,'' Grue breathed the word, stepping down to the depressed pavement and breaking into a run as he headed for the explosion site.  Tattletale gave me a hand in stepping down as we followed.  It wasn't necessary, but I didn't turn her down.



The explosion had shattered one exterior wall of the building, and scorched the inside.  My swarm fanned out to search the building's interior.  It didn't take long to find her on the second floor; she was so caked in dust and debris that I'd almost mistaken her for a piece of wreckage.



``Second floor, near the back.  Stairwell is this way.''



Noelle, I realized, was vomiting from one of the three mouths on her lower body.  The slurry contained a human being, naked, with ulcerous growths all over her body.  Circus.



And Noelle wasn't in contact with Circus.



``Fuck me,'' I said.



``Is she hurt?'' Grue asked.  It took me a second to realize he meant Imp.



I shook my head.  ``I don't know.  I was swearing because\ldots It's Noelle.  She's creating clones, and she apparently doesn't need to be in constant contact to do it.''



``She does,'' Tattletale said.  ``Everything the Travelers said indicated it, and my power corroborated.  She's touched people before and hasn't produced any of them in the time she was with Coil.''



``Maybe it's a short duration thing,'' I said.  We'd reached the staircase.  I was a little slower than my teammates in ascending the stairs.  My stamina was nowhere near where it needed to be, and my chest was aching as I breathed harder.  It made talking harder.  ``She absorbs someone and she can create clones for a little while after.''



``Maybe,'' Tattletale said.



We reached the top of the staircase.  The floor wasn't entirely intact at the landing, so Bitch and her dogs hung back.  With the damage the explosion had done to the exterior wall, I could feel the saltwater scented air stirring my hair.



We reached Imp's side.  She'd slumped against an intact wall.  I worked with Grue to clear away the pieces of wood and concrete that had joined Imp in being thrown against the wall.



``Turn around,'' Tattletale ordered Tecton and Grace.



Tecton listened.  When Grace didn't immediately obey, he grabbed her by the shoulder and forced her around.



Grue took off Imp's mask.  My bugs traced her, and I could sense the trail of blood running from one of her ears.



``Hey,'' Aisha murmured.  ``Owie.''



``Are you hurt?'' I asked.



``Ear hurts.  Hurt all over where I hit the wall.''



``That ear's a ruptured eardrum,'' Tattletale said.



``Shitty,'' Aisha said, ``Least I save money, not having a reason to buy surround sound when I get my own entertainment system.''



``You're not so lucky.  It'll heal,'' Tattletale said.



``Did you hit your head?'' Grue asked.



``No,'' Tattletale and Imp answered in the same moment.



Grue smacked his sister lightly across the head.  ``Idiot!  You're supposed to listen when we give you orders.''



``I know \emph{why} you were giving that order,'' Imp said.  ``You wanted me to clear out in case he smooshed this building.  Except I knew I couldn't get out fast enough.  I figured I'd take out that gun guy.''



``Leet,'' I supplied.



``Leet, yeah.''



Grue cuffed her across the head again.



``Hey!'' Aisha said.  Then she cringed, or winced, as if she was in pain.  ``Ow.''



``What?''



In a quieter voice, she said, ``Ear hurts when I speak too loud.  Stop hitting me.  It was the right call.''



``You still didn't listen,'' Grue said.  He took the mask from Tattletale and helped Aisha put it on.  ``Get up.''



Imp stood, then wobbled.  ``Dizzy.''



``Ruptured eardrum will do that,'' Tattletale said.  ``Let's go.  We should see what we can do to help against Noelle.''



Grue and Tattletale supported Imp between them as we made our way to the stairwell.  I turned my attention to the fight.  ``Eidolon's holding his own.''



``Told you,'' Grace said.



``He's using that pressure--''



``Gravity,'' Tattletale said.



``Right.  He's using supercharged gravity to try to pin her down and simultaneously take out any of the clones she spits out.  He's staying out of reach with flight, and he said something before about a danger sense.  Precognition, I guess?''



``Didn't help him stop the explosion,'' Regent commented.



``It let him move well out of the way before it went off,'' I said.  ``And it's helping him when Noelle tries to trick him.  She's\ldots I don't even know how to put it.  She's \emph{wearing} a Vista that can turn two-dimensional, and the Vista is helping keep her other clones alive.  Whenever Eidolon moves like he's about to drop that gravity magnification on them, she folds Noelle's clones against whatever surface they're touching and then pastes herself into Noelle.''



``Can we help Eidolon by taking the Vista out?'' Grue asked.



``I don't know how we'd get the Vista without attacking Noelle,'' I said.



``Eidolon can hold onto about three serious powers at a time,'' Tecton said.  ``If he's packing flying, danger sense and gravity manipulation, that's it.  Sometimes he does four, but two or three of them are usually pretty minor.  Enhanced accuracy, whatever.''



``Unless the flying's an extension of the gravity manipulation,'' Tattletale pointed out.  ``I'd guess he's maintaining a kind of power immunity, in case Noelle manages to close the distance or one of her underlings tries to hit him from range.''



I could follow the fight as Noelle leaped to another rooftop.  Being airborne, she might have been vulnerable if Eidolon had been able to devote his full attention to her, given how it wasn't possible to dodge while midair, but she'd timed the jump to coincide with a killer-Circus's pyrokinetic attack on Eidolon.



The hero destroyed the Circus with a use of his gravity power, and I could guess that the same power had destroyed any incoming fireballs she'd thrown his way, because he wasn't even touched by any hot air.  The top floor of the building the Circus had been standing on was still collapsing as he directed another gravity-slam in the direction of Noelle's landing point.  She was already moving on, leaping to a building face that Eidolon wouldn't have a line of sight to.



The degree of mobility the pair had meant it was hard to get bugs in a position where I could follow what was going on.  I moved the bugs up through the various buildings, spreading them out as best as I could.



In tracking the movements of the bugs through the buildings, I got a sense of where Eidolon had done damage and where the civilians were.



``He's doing a fantastic job of avoiding hitting any civilians when he uses his powers.''



``Told you,'' Imp said, mimicking Grace's tone, in the same moment Grace said, ``Of course.''



Imp laughed, then winced at the pain it caused her.



``Could be an extension of his danger sense,'' Tattletale suggested.



We'd reached the stairwell, and the others declined to go back for the van.  Imp and I got on Bentley's back.  I sat behind Imp so I could help keep her from falling.  We weren't broadcasting it to Tecton and Grace, but I wasn't in great shape, myself.  Even if Bentley wasn't the most comfortable way to travel with a cracked rib, it still beat running.



I pointed the way, and we headed for the site of the battle.  I wasn't exactly sure what we could do.  This was a fight between titans.  Eidolon had hit Noelle a thousand times as hard as any of us were capable of, and she hadn't even slowed down.



I was getting increasingly worried that there was some factor here that would decide the battle, something I \emph{should} grasp but wasn't.  It didn't help that both Noelle and Eidolon had powersets that I didn't fully understand.  Noelle was apparently pulling clones out of nowhere, despite not having contact with Vista or the other villains.  Getting a sense of any given power and accounting for all the possibilities was hard enough, but Eidolon had a bunch of them at any given time, and they could \emph{change}.



Eidolon struck at one cluster of clones that were lurking in a half-destroyed building, then hit himself with a gravity attack.  He and his costume were left untouched, but the bugs I had on him were annihilated.  I was left blind.



\emph{Why}?  The attack was pointless.  There hadn't been any of Noelle's servants in the area.



Was he sending me a message?  Did he want us to back off?



Noelle was consistently managing to avoid being struck by any of the gravity attacks, or scrambling out of the way of trouble after sustaining a glancing blow.  She was keeping tall buildings between herself and Eidolon.  He used the gravity manipulation where he could.  He had changed up his tactics, sending chunks of building flying, then spiking them down to the ground with the gravity-slams.  He wasn't changing powers, though, even though Noelle had adjusted to them.  It was very possible he \emph{couldn't}: that if he gave up one power for another one more suited for the situation, he'd be too vulnerable while it grew to full power, or it would be too hard to catch up after the fact.



One of the heads of Noelle's lower body vomited up a slurry of flesh, with two naked bodies in the midst of it.  A Vista covered in fingernail-like plates of hard flesh and a Leet with one forearm and hand as big as his torso.  The two clones were on their feet in seconds.  The Vista ran in Eidolon's direction, while the Leet made a beeline for a nearby mall entrance.



I sent a swarm of bugs after them, focusing predominantly on going after Leet.  They weren't \emph{fast}, but they would hopefully interfere with his efforts to build anything.



We arrived at the edge of Eidolon and Noelle's battlefield.  As I drew a swarm together with the bugs in this new area, I found Eidolon and tagged him with some houseflies and wasps.  Best if I knew if he was moving in our direction, so we could clear out of the way.



``Circle around,'' I said.  ``We keep eyes on one another, but our goal is to clean up clones wherever we can, so we need a broad perimeter.''



``Got it,'' Grue said.  Tecton nodded as well.



Rachel signaled, and Bentley ran.  Tecton and Grace moved as one pair, while Regent, Grue and Tattletale formed another group.



The Leet had entered a mall.  The place had been looted, but he stopped somewhere long enough to grab some basic clothes.  He wrenched a piece off a clothing rack and used the ragged end to cut a sleeve off and open up the shoulder enough that he could fit his oversized left hand through it.



The activity bought my bugs enough time to catch up to him.  As they attacked, he started thrashing.  I was in the middle of changing my focus to other things when I noticed something curious.



A rat.



The rat itself wasn't so unusual.  Large for its size, maybe.  But it had moved in the same general direction as my swarm, and it was wet with fluids.



The vomit?



I'd been flying bugs over surfaces at a height sufficient to catch humans.  It was a waste of energy and bugs to fly them over the ground level, when I generally knew that a road was flat, and any obstacle that was shorter than one or two feet wasn't worth dwelling on.



Moving my bugs closer to the ground, I found more.  Rats, wet with the fluids of Noelle's vomit.



She'd absorbed \emph{rats}?  She wasn't limited to cloning people.



I made a point of searching the vermin out and killing them with my bugs.  I'd played exterminator once before.  Not over so large an area, but I'd done it.



I pointed the way to Noelle, and Rachel changed direction.  Eidolon was dealing with the last Vista-clone that Noelle had spawned.  The girl wasn't going on the offensive, but she was using her power to move quickly, using every spare moment to raise lumps of pavement and concrete from the ground, sculpting them into rough images of Noelle.  It would be sunrise, now, but in the dim light, they would be something that distracted Eidolon and potentially drew his fire.



He paused in his attempted murder of the mutant girl and eradication of the statues, striking himself with another gravity-slam.  Again, he killed every insect I had on him.



Was he aware of something we weren't?



Noelle turned toward a group of people who were evacuating one of the buildings that had taken damage.  Before I could open my mouth to shout a warning or take an action, she lunged into the lobby of the building.



The people she touched were absorbed as quickly and easily as if she were quicksand.  Some were almost \emph{drawn} in.



It took a minute and a half for her to form the clones within her.  We closed the distance as her body swelled.  When she'd reached critical mass, each of the three mouths on her lower body opened to heave out a tide of blood and gore, along with eighteen or twenty people.  Half of the people she'd heaved out had clothes.  The other half had mutations.  The mutants were on their feet as soon as they could find traction in the sludge, the innocents seemed as though they could barely move.



One of the people was Vista, I realized.  Not a clone – she was costumed.  An extremity, a tentacle or tongue, extended from one of Noelle's lower mouths to wrap around Vista's midsection.  The girl was hauled into the mouth and swallowed in a flash.



``She's keeping them,'' I said.



``What?'' Tattletale asked.



``The capes she keeps spitting out.  Circus, \"{U}ber, Leet and Vista.  She's holding the four of them inside her, so she can keep creating more clones.''



``She doesn't have to let people go,'' Tattletale said.  ``Fuck me.  We won't be able to kill her without killing whoever she's holding inside her.''



As the mutant clones around Noelle began to thrash and strangle the near-helpless victims, their maker shifted position, stepping on arms and legs.  Her body was oriented more towards Eidolon.  I wasn't willing to sacrifice bugs to know her exact position, but I got the sense she was looking up at him, despite the fact that there were several buildings between her and him.



She made contact with the bugs I had in her immediate vicinity as she twisted her body to look towards us.



Then she ran in the other direction.



``We rescue the people she just vomited out, clear away the clones,'' I said.  I used the bugs I'd gathered near the other two groups to speak to them.  ``Then we signal Eidolon and chase Noelle.  We need to get in contact with the heroes.  Whatever Eidolon's plan is, it's not working.''



I could track the rats that were crawling out of the vomit.  A dozen of them, and they were homing in on people, savagely biting and clawing into any flesh they found.  I made sure to cluster my bugs in as dense a swarm as I could afford, to keep them contained.  The bugs I didn't devote to the task worked to disable and distract the more mundane clones.



I might have missed it if I hadn't had the bugs pressed together to contain the rats.  I \emph{had} missed it already, countless times.  Wasps, hornets and cockroaches were crawling free of the slurry of flesh that Noelle had vomited into the building's lobby.  They were attacking my bugs and any people they found.



I couldn't sense them, and I couldn't control them.





