





I signalled Bitch to stop so I could communicate with the others.



``I fucked up,'' I said.



``What?''  Grue asked.  ``How?''



``She's been absorbing my bugs.  She's spitting out some, and I can't control them.  They're methodically destroying my swarm, and they're hunting down people and attacking them.''



``She probably absorbed some before she even ran into us,'' Tattletale said.  ``And she just needs one of a given type to make copies.  I wouldn't blame yourself.''



``Did she absorb hornets, black widows, brown recluses?''



``Maybe not,'' Tattletale admitted.



``Okay,'' I said.  ``Because there's homicidal hornets and spiders out there now.  Because of my fuck-up.''



``Don't focus on the mistake,'' Grue said, ``Let's focus on making up for it.''



I took a deep breath.  ``Okay.  Bitch and I will be going ahead to deal with some unpowered clones.  I'll be in touch through the swarm.  You guys keep moving forward, and I'll signal you about any clones that Eidolon or my bugs aren't able to take down.''



``Eidolon's gone quiet,'' Tattletale said.  ``He might be changing powers, chasing at a distance to safely keep track of her while he adjusts.''



``I'll try to signal him,'' I said.  ``Let him know we're here, and that we're engaging Noelle if and when we've managed the clones and we see an opportunity.''



``Hopefully he doesn't \emph{accidentally} wipe us off the face of the planet,'' Regent joked.



``Hopefully,'' I echoed him, except I wasn't joking.



``Then I'll suggest that this can be where we part ways,'' Tattletale said.  ``I'll take Imp, I can do more good with a phone and computer, and she's no good to anyone right now.''



I nodded.  I helped Imp climb down to the others.



``Good luck.''



Bitch whistled, and Bentley sprang into motion once more.



The people inside the building lobby were only now starting to recover from whatever Noelle's power had done to them.  Their clones hadn't suffered any such drawbacks, though, and the abuse that had been heaped on the victims was more than making up for their recovery speed.  They were helpless.



None of the victims were standing.  I reached forward, putting one hand on the chain that Rachel was using to keep Bastard close.



She looked back at me.



``Clothesline!'' I raised my voice to be heard over the rushing wind.



Rachel let some chain out and caught it under her left foot, forcing it lower.  She managed to hook it on one of the growths of bone of Bentley's ribcage.



We stampeded into the building lobby, through the hole Noelle had made, and Bitch whistled, flicking the chain as Bentley and Bastard passed through the space.



``Left!'' she shouted, while steering Bentley right.



The chain was just low enough to catch the standing and crouching clones.  The clones were caught by either the chain or by the bodies of their fellow clones, pulled back en-masse, drawn together into a tangle of bodies and distorted body parts.  I moved my bugs through their midst to ensure they were all mutants.  There was only one innocent who'd been dragged long with them.  His clone had a grip on his clothing, and hadn't let go when the chain had caught it.



``Getting down,'' I said, sliding off the dog's back.  I hurried to the mass of clones before they could get themselves in order, drew my knife and slashed the hand that gripped the one innocent.  I managed to pull him free without any of the clones hitting or grabbing me.



I was left coughing by the exertion and the pain in my side.  Bitch steered Bentley to put his bulk between me and the clones.



``I got 'em,'' she said.



``I'll handle the others,'' I told her.



``Right,'' she grunted the word. ``Bastard, hurt 'em!  Bentley, kill!  Kill!''



The canines threw themselves into the mass of clones the chain had caught.



There were three clones in the remaining group.  One continued thrashing her alter-ego, while the other two stood to face me.  I held my knife in one hand, drew my baton with the other and flicked it out to its full length.  Not nearly as threatening as either of the canines, but I'd make do.



It was odd that Rachel was having Bastard hold back, being limited only to a `hurt' command.  Come to think of it, she'd had Bentley do the killing when fighting the Vista-clone, too.



My rib throbbed even now, just from riding Bentley and hauling the one victim out of the mass.  I was left breathing hard, though the exertion had been mild.  My stamina wasn't a tenth of what it might otherwise be, to the point that I was worried I might get dizzy, start coughing or wind up too tired to fight if it came down to a straight hand-to-hand brawl.



I couldn't afford to take it easy, though.  Where I might otherwise have tried to distract them or buy enough time for Bentley to finish off the others and deal with these guys, the person that the female clone at the back was thrashing wasn't going to last long.  The two who were facing me were both men, both bigger and tougher than they might have been as humans, one fat, the other tall and broad-shouldered and narrow-waisted to the point of being a caricature.



My swarm was my best offense and my best defense, here.  My bugs went for eyes and ears, and that was excuse enough for the two mutants to charge me.



They were half blind, and the mass of bugs that clung to me billowed out to mask my location.  I started to move to my left, but I felt the fat one veer slightly in that direction and chose to head between them, instead.



The pair stumbled forward into my swarm, arms swinging wildly in a blind attempt to hit me.  I ducked low, then moved forward to the mass of fallen and wounded.  The female clone had her more normal self by the neck, and was repeatedly raising her and slamming her down.  If someone else's leg wasn't in the way, she might have had her head dashed against the ground.  As it was, a beating was still a beating, and something vital was bound to give sooner or later.



The clone looked up at me as I approached, still cloaked in a thick cloud of bugs. I realized why she hadn't stood to face me.  Her left leg was gone, barely a flipper.  She raised her arms in self defense, and I batted one aside with my baton before stabbing her just above the collarbone.



\emph{They're not people.  They're mockeries.}



The small, helpless sounds she made as blood bubbled around the throat-wound weren't helping my attempts to assuage conscience.



\emph{Damn Noelle, damn her for making me do this.}



``You leave Steph alone!'' the fat clone bellowed.



The words caught me off guard as much as the fact that he'd seen the attack.  He charged, and I swiftly backed up, bringing my weapons to the ready.



He didn't come after me.  He stopped by `Steph', the one-legged clone with the fatal throat wound.



``You care about her?'' I asked.



``She's Steph,'' he said.



``I\ldots what?''  My train of thought was interrupted further by the snarling and gnashing of Bentley fighting the clones.  One tried to break away from the group to come after me, but Bentley caught him, striking him flat against the ground with both front paws, like how a cat might pounce on a mouse.



``She's Steph.  She's Steph.  Of course I care.  Fucking bugs!''  He lashed out with one arm, as if he could hurt the swarm, drive them away.  His arms folded around the clone-Steph.



I pulled the attacking bugs away, leaving only enough to track his movements.  I wasn't sure I \emph{wanted} to open up a line of dialogue, but my conscience couldn't afford to let me \emph{not}.  ``But\ldots what about the person she was beating up?  You don't care about the \emph{real} Steph?''



``Ignored me.  Looked down on me because I was fat.  \emph{Fuck her},'' he spoke with such force that my bugs could feel the spit flying from his mouth.



``She's still Steph, isn't she?''



``Bitch.  Brushing me off.  Made it so we were \emph{friends, }not boyfriend and girlfriend.  Bitch,'' he said.



He let the mutant-clone Steph drop limp to the ground, clenched and unclenched a fist.  ``Fuck her.  Fuck you for killing Steph.''



``Why do this?  Why hurt people?''



``I'm a soldier,'' he said, his words dull.  ``It's what I am.''



I sensed his girth, used my swarm to sense his equally heavy alter-ego.  ``You\ldots don't strike me as a soldier.''



``It's what I am.''



``Is\ldots is \emph{he} a soldier?'' I gestured in the direction of his other self.



``No.  Fat fuck could never be a soldier.  Kill him.  Dig my fingers into that gut and rip and tear until he dies.  Strangle him.  No willpower, hide from the world behind that disgusting \emph{fat}.  Choke the life out of him.  He's useless anyways.  Waste of air, waste of a life.''



\emph{Projecting much?}



``And when he's dead?  What will you do?''



He moved toward me, and I backed away a step, bringing my bugs closer to him.  He went still again, glanced around.  ``Kill others.  Kill Dad and Mom and Sammy and the cats.  Kill teachers and classmates and burn my house and burn the school.  Fuckers.  All of them.  Looking down on me.''



His words struck a chord, and it was the closest experience I'd ever had to the sort of flashback that happened in the movies.  I could remember being in the school bathroom, dripping with juice.  Being so frustrated, so angry, so hurt that I just wanted to lash out.



Was that all he had left?  Was that all he was?



``And if \emph{they} all die?''



``Kill others.  Burn this fucking disgusting city.  Burn this fucking country.  Keep burning, keep killing.''



``Do you really think that'll make anything better?''



``No.''



``Then why?  Is there any way I can get you to stop?''



``No.  Won't stop.  I'm a \emph{soldier}.''



``Whose soldier?  Hers? Noelle's?  The monster who spat you out?''



``No.''



``And you?'' I asked, turning so my back wasn't to the broad shouldered one in the midst of my swarm.



He didn't answer.  He charged for me instead.  The obese one took the opportunity to come after me from a different angle.



Again, I drew my swarm around me, put each of my bugs on the offensive to distract, and used my swarm-sense to figure out where they were moving, getting out of the way.



Ducking low, I felt a sharp pain in my side.  I grunted in pain and barked out a cough.  The cough made me need to cough \emph{more}, which only helped inform them of my position.



The coughing fit took the strength out of me at a time when I needed to move most.  Swimging blindly, the fat one struck me across the face.  My mask absorbed the worst of the impact, and I stuck my knife out in his general direction, sticking it into the general area of his chest, hitting bone rather than anything substantial.



``Bugs fucking hurt,'' he growled, apparently oblivious to the pain of the knife wound.  ``Stop it!''



He swung again, but I managed to get out of the way.  With the stinging, biting insects in his eyes, crawling into his mouth and nose as he talked to gag him, I managed to distract him enough that I could safely retreat.  My entire body shook as I suppressed coughs, and I dropped to one knee to try and catch my breath.  I hoped that being closer to the ground would mean I didn't get hit; I was too breathless to move out of the way if he swung a punch at me.



The broad-shouldered one stepped close, his cheeks wet with the vitreous fluids of torn eyeballs and blood where my swarm had dug in deep.  I suppressed another cough and slid my knife's blade against the back of his knees.  It might not have cut deep enough if he'd been wearing clothes, but he was naked, and there was nothing to stop the knife.



He collapsed just in front of me.  I hesitated a moment, then stabbed my knife into the side of his throat.



\emph{They're not real}.  \emph{Not real people}.



Bentley had finished tearing apart the other eight or so clones, and at Rachel's instruction was closing in on the fat clone.  I moved my bugs to give her a clearer view.



I was ready for him to make a break for it.  He didn't.  He turned toward us, clenching and unclenching his fist.



\emph{There's no saving them.  Whatever had happened to their heads while they were grown inside Noelle, they're twisted.  Their perspectives are warped.}



``Stop him,'' I said.  ``Finish them, Rachel.''



Rachel whistled, and Bentley leaped.  The clone tried to come after me, but didn't make it two steps before the dog got to him.



``Feels wrong,'' I said.  Rachel gave me a hand in climbing back up.



She didn't offer a reply.  It wouldn't feel wrong to her.



I started searching with my bugs, looking in the direction Noelle had last gone.



Without even the ability to tentatively feel Noelle out with my bugs, I was having trouble keeping track of her.  Every passing minute meant that there was more sunlight, but even with that I couldn't \emph{see} Noelle.  It was as though a painter was working with white and black paint, throwing handfuls of it onto a canvas from three feet away.  It didn't convey a \emph{picture} so much as a blurry, indistinct abstract.



I \emph{should} have been able to follow \emph{movement}, to track Noelle by the way the patches of light and dark \emph{changed}.  The issue was that there were countless things moving across my radius.  Water was running where some streets were still draining, plastic bags blew in the wind and shadows shifted as the sun and clouds moved.  Each changed the canvas, altered the blurry, muddy blotches of light and dark.



I could hear Grue give an order, and his group started moving with purpose.



``Grue just saw her, I think,'' I said.  I pointed the way.



I'd started another coughing fit by the time we caught up with the others, and I could feel my skull pounding as if it had a three pound heart inside of it instead of a brain.



``She found some of the other capes who were holding position,'' Grue said, when I'd managed to get my breath.  ``Lights in the distance.''



``Fuck,'' I said.  I was about to comment on how we were too close to Ballistic's headquarters for comfort, but remembered that Grace and Tecton were listening.  I stopped myself before the words left my mouth and coughed instead.



``You okay?'' Tecton asked.



``Little worse for wear.''



``Sounds like more than a little.''



I shook my head.



As we got closer, I tentatively moved the bugs closer, until I had them on the flying heroes.  I made an effort to discover and eliminate the hostile bugs that Noelle had created, and tried to find identifying details on the capes we were approaching.



``One of the heroes is a guy with an emblem, I think it's a book with chains around it,'' I said.



``Maybe Chronicler,'' Tecton said.



``Three more flying ones,'' I said.  ``One with antlers on his chest emblem.''



``All guys?'' Tecton asked.  When I nodded, he said, ``That'd be Strapping Lad, Intrepid, and Young Buck.  And the one you mentioned before would definitely be Chronicler.''



``Seriously?'' Regent asked.  ``\emph{Strapping Lad}?''



``They're from the Texas Wards team,'' Tecton said, as if that was explanation enough.  ``Lad, Intrepid and Buck are all about the harassment.  Flying, teamwork, hitting hard and adjusting their battle plans to match the enemy threat level, staying out of danger.''



``Up until they get too close and she grabs one,'' I said.



``Could happen,'' Tecton replied.  ``Eidolon's probably up there too, too quiet.  Might be waiting for new powers to finish manifesting before he makes any moves.''



``What can we do?'' Grace asked.



``I remember those Wards from the Leviathan fight.  Some of them,'' I said.  ``They fly?  All of them?''



``Yeah,'' Tecton said.



``Then we support on the ground,'' I said.  ``You, Grue and maybe Regent can slow her down.  Bitch keeps us mobile.  We stay ready to move at a moment's notice if it comes down to it.  Staying safe is a bigger priority than anything else.''



Noelle was limited to moving on the ground.  It gave the young heroes a natural advantage: each of them flew, and two of the three were armed with long ranged tinker-made weapons.  The guns weren't anything flashy or spectacular, more the kind of laser weapon that a fan of science fiction might create, but the young heroes apparently thought it was worth keeping up the onslaught, and the guns didn't appear to rely on any ammunition or reloading.



The one without the gun was apparently Young Buck, going by the raised image of antlers on his chest emblem.  He would fly around Noelle, close to the ground, then turn himself, his gear and the bugs I'd placed on him into a living projectile.  Or, maybe, he was using some kind of uncontrolled breaker power to go faster than the speed of sound, unable to change course or take any action while he traveled.  Whatever he was doing, he flashed across the battlefield as a straight, living projectile before materializing again.  The ground shook with his impacts he delivered to Noelle.



The one I took to be Chronicler was casting out a hazy field around himself and the other two with the guns.  The field shifted, drifting closer to the ground, and then solidified in a semisolid image of the heroes, complete with the laser fire.  A quick check with my bugs verified that the shots were just as real as what the real selves were creating.  The aim wasn't so hot.  It was more of a replay of the actions they'd just taken than proper \emph{clones}.



Young Buck moved beneath Chronicler, and passed through the field as he turned into a beam.  When the images appeared, they mimicked the same beam attack, their paths a perfect parallel to the real Young Buck.



We stopped as she came into view.  For the others, anyways.



``Fuck me,'' Regent said.  ``Anyone else noticing what I notice?''



``Bitch's dogs,'' Grue said.



``Not \emph{that} similar,'' Rachel grumbled, but she didn't sound confident.



``Pretty fucking similar,'' Regent said.



I leaned forward, hand on Rachel's shoulder, whispered, ``What is it?''



``Her entire lower half, it looks like my dogs.  Bit on the back doesn't look like it, though.  More like a hand, but same look.''



``Thanks,'' I replied.



``We good to go?'' Grue asked.



``Go,'' I gave the order.



Tecton slammed his piledriver-gauntlets into the ground, and a fissure opened beneath Noelle.  The ground shattered around her, denying her the footing to move out of the way as Chronicler and Young Buck worked together to multiply Young Buck's offensive power.  Tecton repeated the process, disintegrating the ground beneath her.



``I can't do a lot to her,'' Regent said.  ``Only some of her is normal, and it doesn't really connect together.''



``Try, or focus on the clones,'' Grue ordered.  He sent a blast of darkness my way, enveloping me.  I could feel the quality of my bug-senses decline, my degree of control degrading.



A moment later, he withdrew the darkness.  Did he just want the view?  The sense of what was where?



Raising his hands above his head, Grue fired a thick stream of darkness at Eidolon.



The hero moved out of the way before the beam made contact.



``Work with me!'' Grue growled.  ``Damn.  I can't throw darkness over Noelle without hurting our side as much as we hurt her.  I need powers.  Grace?''



``You want to copy \emph{my} power?''



There was a rumble as Tecton shattered more road beneath Noelle.  With the way he'd directed the attack to place it off to one side, I suspected she was trying to climb out of the funnel-shaped depression the explosions had made.  Given her speed from before, it was surprising how slowly she was climbing.



Then it struck me. \emph{ An antlion pit}.  The sides of the pit weren't giving her any traction.  Any time she set her weight down, she only pushed the sand to the bottom.



``Let me test it, see what I can get,'' Grue told Grace.



``Fine.''



I scouted the area with my bugs, and accidentally ran into Noelle with a handful of houseflies as she slid backwards into the pit.  I wasn't going to agonize over the fact, but I didn't want to give her any more ammunition.  My bugs \emph{did} find a mess of vomit at the very bottom of the shallow crater.



``There's vomit, but no clones,'' I said.  ``She's trying something.''



``The two-dimensional Vista.  She's ambushing,'' Grue said.



``Ambushing who?''  Tecton asked.



``I don't know.  Can you see them?'' I asked.  ``When they're moving on a surface, are they visible?''



``Why are you asking \emph{us}?'' Grace asked.



``Tecton,'' I said, ``As much ground as you can affect, \emph{now}!''



He didn't hesitate, punching the ground and driving both piledrivers into it.  There were no fissures, this time.  The entire area rumbled, and the ground spiderwebbed with cracks in every direction, not leaving two square feet of ground untouched.  Bentley nearly lost his footing, and Bastard growled, until Rachel pulled on his chain.



The first clone stepped out of a piece of plywood that had been placed across a shattered balcony door.  An \"{U}ber.  He pulled the plywood free and disappeared into the apartment, swatting at the bugs that I'd set on him.



A Circus emerged beneath the flying heroes, cradling a shattered arm.  Bugs began drifting toward her, as if a strong wind were pulling them in.  The normal Circus packed a pocket dimension she could put things into.  This one was only storing \emph{air}, forming a strong vacuum around herself.  Chronicler's cloud dissipated as it was sucked in, and the heroes with weaker flying abilities were swiftly being dragged her way.  Regent hit her with his power, and the effect slowed, but she recovered faster than the fliers did.



My swarm could see a large blob of shadow, Noelle, taking advantage of the distraction to climb free of Tecton's antlion pit.



``Now!'' Grue said.



Grace ran forward, having little trouble moving on the shattered road.  She leaped and kicked Noelle, no doubt putting her invincibility in one foot.  As the kick was delivered, Grace used Noelle as a foothold and thrust herself away.  Grue chased her attack with a stream of darkness, enveloping Grace as she stuck her landing, leaped, and did very much the same thing Grace had, slamming one fist into Noelle.



Noelle toppled with a rumble my bugs could feel, then slowly slid back into the crater Tecton had made before she could get her feet under her again.



The \"{U}ber stepped out onto the balcony with a block of kitchen knives in hand.  Though they weren't weighted for throwing, he had no problem throwing a knife to hit Young Buck as the hero flew by.  Young Buck spiralled out of the air, stopping himself only a moment before he hit the ground.  When he righted himself, his hands were pressed around the knife that had embedded in his stomach.



I sent more bugs after the \"{U}ber, my bugs tearing at his eyes and hands in earnest.  He threw another knife blind, hitting Chronicler in the arm before he collapsed and started thrashing to get the bugs off himself.



The Circus, for her part, had used her pocket-dimension vacuum to draw one of the fliers close enough to get her hands on him.  The hero, Intrepid or Strapping Lad, was set aflame from head to toe, his costume ignited in entirety.  He kicked out, blind in the midst of the flames that were immolating him, and she ducked out of the way.



Grace saw the flames of the burning hero as Grue banished his darkness.  She made a break for the Circus.  Regent knocked the Circus off balance, momentarily interrupting the suction yet again, and Grace punched with enough force to cave in the clone's chest.  The Circus dropped to the ground, dead.



Grace couldn't see in Grue's darkness, so they were limited as far as their partnership went.  He backed away slowly, searching for another opportunity or another power he could borrow.  Without Grace's natural agility, the individual pieces of road made for unsteady footing, each tilting and sliding as weight was placed on them.



Noelle screamed with frustration and rage.  As far as I could tell, she was still at the bottom of the pit.



I couldn't follow what was happening, not without giving her more bugs to work with, but then again, I wasn't sure that anyone else was having more luck on that front.  Not with the pit around her.



``She's pulling something!'' Tecton shouted.  He raised his voice to be heard by the other capes, ``Get back!''



Everyone moved away, excepting Young Buck, who was frozen, hands to his wound.  Grace retreated, holding onto the incinerated young hero.



When Noelle vomited, the slurry came out as one stream, a geyser that extended six or seven hundred feet.  Rachel steered Bentley out of the way before it hit, and the others danced off to either side to avoid getting splashed.  Grace got clipped, and went sprawling, almost glued to the ground under the weight of the fluid, the cape in her arms falling.



A dozen bodies began climbing free of the vomit.  Ten or so clones had been deposited on the street, along with a real Leet in civilian clothes.  One of the clones was a Circus, folding \emph{herself} into her pocket dimension.



``She's walking on the bodies,'' Tecton said.  ``Incoming!''



\emph{The bodies.  She vomited bodies into the pit to keep stuff from sliding underfoot.}



Young Buck charged through Noelle, but he wasn't flying when he finished his maneuver.  He tumbled to the ground, rolling after he landed.



I could hear armbands informing others of the fallen.



My arm jerked in pain, and I slapped at a hornet.  One of Noelle's.



Noelle advanced on the burned cape and Grace.  Tecton slammed the ground, but the effect was muffled.  He'd shattered the ground for blocks around, had maybe killed or eliminated several of the two dimensional clones, but his piledriver gauntlets wouldn't be as effective on this soft surface.



Two of the Southern Wards opened fire from above, pelting Noelle with laser fire.  I could sense her growing tall, or rearing up on her hind legs, and she vomited a stream into the air.  Chronicler and the other cape were splashed, caught by the clotted liquid and a flying body.  Chronicler's power remained, the hologram images sustaining the same fire at the same angle, not adjusting as Noelle moved to one side.



Eidolon made his move.  My bugs could sense the air growing heavy and humid.  Vomit dried, and clones staggered and fell.



The humidity increased to the point that I could feel the moisture flowing through the air in thick clouds, rising from every surface, heavy off the bodies of the clone, off Noelle and the streams of vomit.



My bugs were dying.  The flying insects were first to die, their wings crinkling.  The ones closest to me were alive, but they were suffering too.



\emph{Dessication}.



``You're killing Grace!'' Tecton bellowed at the sky.  I doubted Eidolon would hear from his vantage point.  I had only his word to go by.  Grace was in an area my bugs couldn't reach.



``Acceptable losses,'' Grue said.  Tecton whirled around to face him.  Grue's voice was calm, ``His plan isn't working.  Tattletale said he wanted to experience enough danger to get a power boost, and I'm not getting the feeling he's had that.  He's too experienced to panic, but with everything he's seen, everything he's done over the past decades of work, maybe he's thinking he has to do \emph{something} here, and he's decided he can't let there be another Endbringer.  Can't let there be another monster in this world.''



``She's on \emph{our} side!  She's one of the good ones!''



``If it makes you feel any better,'' I said, ``Eidolon might be assuming she's already dead.''



I'd positioned some bugs so that they could distinguish Noelle's vague lumbering frame against the background of the dimly lit sky.  Her flesh was drying and flaking off in chunks as the moisture was pulled out with force.



But the ground still rumbled with the vibrations of her steady advance, and for all the dried flesh that was falling free, she wasn't getting noticeably smaller to my bugs' senses.



Eidolon hit her with a gravity slam.  More flesh came free.  I saw a change, with that, but the edges of the silhouette filled in.



``She isn't dying?'' I asked, my voice a murmur.



``She's regenerating,'' Grue said.



The effects of Eidolon's dessication were starting to get to me.  The air was too dry.  I coughed once and briefly held my breath to keep from succumbing to another fit.



There was a sound like a firecracker taking flight, and Noelle lurched.  Even with my bug's less than stellar sight, I could see the aftermath.  A hundred slightly different angles.  Noelle's true body, the human half perched on top of the monster, arched her back, her chest out, head turning toward the sky.  A spray of blood and gore marked a small explosion ripping out the front of her chest.



And another, a shot from behind, tearing through her cranium.



My bugs ventured into the dessicated area.  They would only last for a minute at best, but they'd serve to scout, to give me eyes.  They found Ballistic.



He hadn't come alone.  Scrub was with him, and Trickster swapped rubble out of the area to move his teammates in.  He swapped himself in for Grace, appearing in the middle of the vomit-slurry.



I opened my mouth to speak, coughed at the dry air instead.



``You decided to help?'' Grue called out.



``She's our responsibility,'' Genesis said, ``We made a promise to each other.  To get home, no matter what it took.  But there were other parts to it.  Things we added on when the whole situation became clear.  Fixing Noelle was one of those additions.''



\emph{Getting home?}



``We knew it was fucked up,'' Sundancer said.  ``But we promised ourselves that if it came down to it, we'd step in before it got bad.  And this is bad.  So we're acting on it.''



Her orb burned above her head.  Its crackle sounded slightly different in the dry air.



Noelle's growl was accented by a noise from one of the larger canine mouths.  ``Traitors.''



\emph{She's alive.  Shot through the heart and brain, and she's talking.}



``If you were thinking straight, you'd agree with us,'' Genesis said.  ``You'd agree this is right.  That we can't let people get hurt, just for your revenge.''



``I didn't ask for this,'' Noelle said.



``I know,'' Trickster spoke.  He looked up toward the sky, tilted his head, and then Eidolon disappeared.  I could sense Eidolon's new location, a few blocks away.  He tried to fly closer, and Trickster teleported him again, keeping him a distance away.  Eidolon had given up his power invulnerability.



``I\ldots I'll use my sun, Noelle,'' Sundancer said.  ``We'll burn you.  It'll be complete, thorough.  And this ends.  There'll be no more hurting people.  And we put all this behind us, remember you the way you \emph{were}.  It's better if it's \emph{us}.''



``I don't want to be a memory,'' Noelle said.



``You already are,'' Ballistic said, from behind her.



She turned, and a low growl sounded from one of her lower mouths, deep enough I could \emph{feel} the rumble of it.



Ballistic shook his head.  ``The old Noelle's long gone.  Do you think \emph{she} would have survived getting shot like that?''



Noelle didn't answer.



``You have her memories, nothing more,'' Trickster said.



``Krouse,'' Noelle said.  ``\emph{You} turn on me like this?''



``I don't know what else to do.''  He teleported Eidolon away again.  This time Eidolon stayed put.  Choosing a new power?



``You did this to me.  This?  The \emph{old} Noelle disappearing?  It's your fault.  You know it.  You \emph{created me}.''



He'd created her?



He'd dosed her.



``Yeah,'' Trickster said.  He lit a cigarette, put it in the mouth-hole of his mask.



``And I listened to you.  I bought your promises.  Your hollow assurances.  I listened and cooperated when you said I should be locked up.  I listened when they shut me in that vault, in the dark, alone, with that \emph{fucking }beeping that wouldn't let me sleep.  I waited all this time because \emph{you} said I could get better.''



``I know.  It eats away at me.  But I don't know what else to do.''



``I spent the past two years listening to you.  Doing what you wanted.  Just do what I want here, and I'll let it all end.  I'll let her burn me, and then you guys can find your own way home.''



``I know what you want,'' he said, ``But the consequences-''



``-Don't matter,'' she said.  ``It's not our world.  It's\ldots it's as screwed up as the things I make.  They're just dark twisted copies of people in this dark, twisted, fucked up world.''



``No'-'' He started.



``You owe me this.''



Trickster sighed, spat out the barely-touched cigarette.  Even though I couldn't identify tone, I felt a cold feeling in the pit of my stomach.



``\emph{Shit},'' I said.  ``Grue-''



Trickster was already turning.  Grue was only beginning to raise a cloud of darkness around us when he disappeared, Trickster standing in his place.



``Grue!'' I screamed.  He was where Trickster had been, half a city block away from Noelle.



Noelle lunged.  Trickster could have moved out of the way fast enough.  Grue wasn't so lucky.  The shattered ground under her feet shifted, and she slammed into him, her lower body catching Grue, adhering to him.



He was giving her\emph{ us.}



Trickster was already gone from the midst of our group. There was gunfire and incoherent shouting as people tried to identify his location.  Ballistic was gone, replaced by a piece of rubble.  He was taking the most immediate threats out of the picture.  Eidolon, Ballistic, Grue\ldots



Who came next on that hierarchy?



Me.



I found myself only five paces away from Noelle, plucked from the midst of my cloud of bugs.  There were too few to hide me from Trickster's sight, with the way the dessication had thinned their ranks.



She caught me with the back of one claw.  There was a sound like a gunshot going off, my ribs feeling like my bones had turned to white-hot brands, and I \emph{stuck}.  She set her claw down on the ground, and my back exploded with pain as I struggled to contort my body, get in a position where I wasn't being folded in half under the weight of an eight ton monstrosity.



I was spared being snapped in two not by my own struggles, but by the pull of her flesh as it folded around me.  It simultaneously consumed me and pulled on me, as if by a hundred hands.  The process was smooth and inevitable, flesh flowing around me like hot candlewax, even as I was drawn upward and inward.



I could sense Regent appearing nearby.  Noelle turned to face him.  He didn't fight, didn't try to run.  He said something, but I couldn't make out the words, couldn't hear them with the dark, hot, rancid-smelling flesh that had enveloped me.



The last of the flesh closed behind me, my power stopped working, and I was left with only absolute darkness and the pounding flow of Noelle's blood in my ears.





