





``I am Kevin Norton, and I am the most powerful man in the world.''



Kevin made a hand signal, and Duke woofed lightly.



``I've saved millions of lives.  \emph{Billions.''}



Another hand signal bidding another small woof of agreement.



He held out his mug, but the pedestrians around him simply avoided him, ignored it.



The sole of Kevin Norton's old shoe had come free at the toe a few days ago, and the tip of it dipped too low, catching on the cobblestone path. He tripped and nearly fell, and Duke danced out of the way, ears perked in alarm.



Kevin caught his balance by grabbing onto a bystander, a woman, and she almost thrust him away, her face suddenly etched in disgust.



``Sorry about that, miss,'' Kevin told her, as she hurried on her way, quickening her pace.  When he didn't get a response, he raised his voice so she could hear him as he finished, ``A sad thing, that a man of my stature can't afford \emph{shoes}, isn't it?''



Kevin's gait bordered on a limp as he adjusted his walk to avoid tripping on his shoe again.  The path here was old-fashioned, cobblestones worn by the tread of hundreds of people over countless years.  The area around him wasn't so old.  Renovated storefronts and new buildings were popping up, mimicking the older British styles while staying current, fresh and new.



``We won't be able to stay for long, Duke,'' Kevin said.  ``Amount of money the city's dropping here, they won't want vagrants around.  But I only want to pay a visit to my old haunt, see what's become of it.''



He saw a family approaching, held out a mug, ``A few pence, for the most powerful man in the world?''



The kids stared, but the parents averted their eyes, the mother putting her hands around the little one's shoulders as if to protect them.



Kevin shrugged and walked on.  There were only a handful of coins inside the mug, rattling around as his arm swung.



``You wouldn't remember much of this area,'' he told Duke, ``I'd already moved on from this before I found you.  Ran.  I'd pass through a few times when you were still small enough to hold in my hand, but I'd avoid this particular spot.  Won't say I haven't missed it.  The old owners used to give me some of the leftovers.''



He pointed, ``Just over there, there was a bakery.  They'd throw out anything more than a day old.  \emph{Bags} of rolls and pastries.  Sausage rolls, pasties.  When they realized I was coming by to partake, supplement my meager diet, they started leaving the bags to one side of the bins so it wouldn't get soiled, and they'd leave other things.  Little things.  Some salads, so I had some greens.  A comb, a toothbrush, soap, deodorant.  Gentle folk.''



Kevin reached down to scratch the top of Duke's head.



``Wonder what's become of them.  Hope the changes around here treated them alright.  Be a crying shame if they were forced out and didn't get what their shops were worth.  They deserved that much, at least.  More.''



Duke yawned, and ended the yawn with a little whine.



``Me, you ask?'' Kevin said.  ``No.  I don't deserve much of anything.  What's that line, about power and responsibility?  Most powerful man in the world, I have a bloody \emph{great deal} of responsibility.  Sure, I go to bed hungry, I slept terribly during that one spell of body lice, but the thing that \emph{really} costs me sleep is the idea I might have shirked my responsibilities.''



Kevin looked down and Duke met his eyes, tilted his head quizzically.



``I got scared, boy.  Because I'm a coward.  There's three good ways to get to where I'm at in life.  Not talking about being the most powerful man in the world.  Talking about how I don't have a place to go, not a friend in the world besides you.  One way you get like this is a lack of support.  Caring family, friends, you can get through almost anything.  No one there to back you up?  Even the littlest things can knock you down a long way if there's nobody to catch you.''



There was a dull rumble, and then the rain started pouring down, heavy.



``A summer rain, Duke.  About due, isn't it?''



The few people on the streets ran for cover, and the little side street was nearly emptied in the span of a minute.  Kevin stretched his arms, letting the rain soak through him.  He dragged his fingers through his hair to comb it back, raised his head to face the sky.



Duke shook himself after only a few seconds, spraying water.  It startled Kevin from his reverie.



``What was I saying?  Oh, right.  Second way you get to circumstances like mine?  Sickness.  Sometimes that's in the head, sometimes it's in the body, and sometimes it's a sickness you get in a bottle or a pipe.  Third path is the one I took.  Cowardice.  Run away from life.  Run away from yourself.  Sometimes the bottle's a cowardice too.  Run away from the truth about what you're doing to yourself, I dunno.  I have you to thank for sparing me that sin.''



He felt a cold wind and stepped under the eaves of the newly renovated buildings, to find brief shelter from the downpour as he walked.



``Too set in my ways to change, to live a braver life.  Just coming back here is taking all the courage I can sum up.''



Duke forced his head under Kevin's hand, and Kevin couldn't help but smile.



``Good boy, good boy.  Appreciate the moral support.''



They had to step out into the rain again to cross the street.  Kevin quickened his pace, and Duke loped alongside him.



He ducked under the next set of eaves as he reached the next block.  ``I fucked up, Duke.  I know that.  I gotta live with that.  I did a lot.  More than most would, I think.  But it's not enough.  If my gut's right, it's not nearly enough.  Shit.''



Just down the street, a shop door opened and a young woman stepped outside.  Petite, pretty, twenty-something, her black hair cut to a pixie cut and topped by a dark gray beret.  Black tights, short, pleated gray skirt.  Fashionable.  She turned his way, an umbrella in hand.



He smiled at her, stepped out into the rain as they crossed paths, so she wouldn't have to.



``Mister?'' she called out.



He was just returning to the shelter of the eaves.  ``What is it?''



``Here,'' she said.  She had her wallet out, and handed him a ten pound note.  He glanced at her.



Taking the note, he said, ``Thank you.''



``You're very welcome.''



He gave her a funny look.  She was looking him in the eyes.  ``Usually I get two types.  Some give me the money and don't even give me a second glance.  Those who do look at me are sure to lecture me on how I should spend it.  So feel free to wag your finger at me, tell me I shouldn't spend it on drugs, drink and fags.  I'll understand, and I can look suitably ashamed.''



``Spend it however you need,'' she said.  She had a trace of a french accent, ``Circumstances might be hard enough that maybe you need to find the little comforts, even if they aren't good for you.''



``Too true.  Rest assured, I feed Duke first, feed myself, and then I buy the little comforts, as you put it.  I admit I do like a fag when I can get my hands on one.''



``Glad to hear it,'' she said, smiling.  ``Hello Duke.''



``He's a good boy, but I wouldn't advise petting him.''



She withdrew her hand.



``Not fleas or anything like that.  I keep him healthy.  But he's a working mutt.  Watches my back when I need watching.  We take care of each other.  So he might be protective of me, not keen on someone getting too close, too soon.''



``Did you name him?'' she asked.  When he nodded, she asked, ``Any reason for Duke?''



``Thought long and hard about it.  Duke seemed fitting.  Highest rank of our United Kingdom, just beneath a king in status.  Fitting for the dog that serves the most powerful man in the world.''



He was looking at her eyes when he said it, saw the sadness in her expression.  ``The most powerful man in the world?''



``It's true.  Don't think I didn't see that.  You don't believe me.''



``It's a grand claim, Mister\ldots''



``Kevin.  Kevin Norton.  And don't mind my rambling.''



``Lisette,'' she said, extending a hand.



He shook it.  Even with the moisture of the downpour, her hand was warm.



``Are you okay?'' she asked.



``Hm?'' he perked up, withdrawing his hand.



``You had a look on your face.''



``Just wondering when the last time I had contact with another person was.  Might have been a few years ago.  Pastor gave me a hug as I left his shelter.''



``That sounds so lonely, Kevin.  Years without human contact?''



``Not so lonely.  I've got one friend,'' he said, scratching Duke's head.



Lisette nodded.



``But you shouldn't forget.  The little stuff.  Even a handshake?  That's something special.  Meaningful.  Value it, even if you get it every day.''



``I'll keep that in mind,'' she smiled.



``Can't tell you how grateful I am,'' Kevin said.  ``Taking the time for me, it means the world to me.  Might be the push I need.''



``For what?''



``I'm looking back, and I haven't looked back in a long while.  Visiting home, so to speak.  Thinking about stuff I haven't even told Duke about, these past twelve years.  You've given me a bump of morale at a time I needed it.  Thank you.''



``I'm glad.  I hope you make peace with it.''



``Heavy burden, mine.  I\ldots I don't suppose you have a little while?  Would you walk with me a few minutes?''



She glanced over her shoulder in the direction she'd been headed, ``My train--''



``I understand if you wouldn't want to.  But if you indulged this old man, it'd make all the difference in my facing this, today.  A few minutes.''



``You're not \emph{that} old.''  She paused.  ``I suppose I could.''



``Come, then, it isn't far.  You might want to open that umbrella.''



She gave him a dubious glance.



He shook his head, ``No.  Not expecting you to share.  I haven't washed my clothes too recently.  Wouldn't want to inflict that on you.  And Duke might get jealous.''



She nodded, and followed alongside him as he headed on his way.  He didn't miss the wide berth she gave him, staying several paces away, hanging back just enough that she could keep an eye on him, as though ready to run if he did something.  \emph{She might be a kind person, but she isn't stupid.}



``I was in my early twenties when I started out,'' he said.  ``Born in London, had nobody left after my parents died in my teens.  Moved up here to York.  Met a girl, moved into her flat.  I won't say it was the cause of this predicament of mine, I'm willing to take the blame for being where I'm at.  But it started me on that road.''



``What happened?''



``Too many mistakes all together.  She wasn't the right girl, for one.  Our relationship progressed, and I realized that I don't like women.''



``Oh,'' Lisette said.



``A little late, but I'd gotten that far by doing what I thought I was \emph{supposed} to be doing, and dating a girl was one of those things.  Am I bothering you?  Boring you?''



``No.  Not at all.''



``Well, I was a young, stupid twenty year old boy, I'd moved in without anything putting my name on the lease and without holding on to any money to move out.  She realized we weren't going to work out, threatened to kick me out, and I begged to stay.  Nowhere to go.  Thought I could save up enough to get a place, if I stuck it out, dealt with the anger.  She started hitting me.  I was never the type to hit back.  It got bad.''



``I'm sorry.''



``There's battered women's shelters, but none for battered men, far as I know.  People somehow imagine a woman couldn't ever strike a man.''



``You left?''



``And I've wondered for a long time if I made the right decision,'' Kevin said.  ``Here we are.''



The road ended, and they reached a narrow stream that fed into the River Ouse.  A small, quaint bridge extended the cobblestone footpath over the stream, benches stood out on a stone patio, and younger trees had been planted in soil bordered by circles of stone.



``\emph{This} is the home you haven't returned to?'' Lisette asked.



``Closest to home I ever had,'' Kevin stepped away from the umbrella's shelter, approached the bridge, ``They changed it.  Used to be I could sleep under here.  It's where I came when I left that apartment and that girl.''



``And you've been on the streets ever since?''



``Some stays in shelters, when it got too cold, and when they'd take Duke in as well.  Have to make some concessions to make it as long as I have.  Thank you, by the way, for coming.  I know you missed your train.  I don't know if I would have been brave enough to go through with this, even with Duke at my side.  I've started and stopped more times than I can count.  It's appreciated.''



She gave him a funny look.  ``It's alright.  Take your time.''



Kevin nodded, ``Would you take Duke?  Just for a minute?''



She took the offered leash, a rope cord that had been carefully knotted into a harness for Duke, extending from his shoulder.  It was barely necessary.  Duke never pulled.



Kevin approached the bridge, traced his fingers over the rounded stones that made up the bridge, the rain-worn gargoyle's face that stood out from the pillar at the bottom.  The rain streamed off the stone face, poured off and through his clothes, soaking him to his core.  It seemed almost fitting.



There wasn't much point, given the rain, but he knelt by the water's edge, where the surface frothed with both current and the downpour, washed his hands.  He took a deep breath, taking in the faint but familiar smells of the river water.  A natural smell.



Memories came flooding back.



Kevin pushed his hair out of the way of his face, cupped water in his hands, and splashed his face.



He stood, then stopped, frozen.



A sigh passed through his lips, drowned out by the noise of the pounding rain.



Between the nearest patio table and tree, the golden man floated, only inches above the ground, luminescent in the gloom and pouring rain.  The light reflected off the falling raindrops, scintillating, cast eerie reflections in the river, and the water that streamed between the cobblestones.



Kevin put his hands in his pockets to warm them, glanced at Lisette and Duke.  Duke hadn't budged an inch, but his ears were flat against his head.  Lisette had her hands to her mouth, eyes wide.  The umbrella had fallen to the ground, forgotten.



Kevin studied the man.  Ageless, the golden man hadn't changed in the slightest.  His hair was the same length, as was his short beard.  Every part of him was a burnished gold, even his eyes.  He didn't breathe, didn't blink as he stared.



The water ran off the golden man's body, but he wasn't getting wet.  His hair barely moved as the rain struck it, his costume absorbed the moisture, but dried just as fast.  The water simply wicked off his skin and hair, leaving him untouched.



It was this same effect that kept the costume clean, a simple white bodysuit extending to biceps and toes.  It had been soiled countless times, by everything under the sun, but the golden radiance the man gave off pushed away the particles, slowly and surely cleaning it just as it was doing with the water.  The suit might as well have been a part of him, now.



``Hello old friend,'' Kevin said.



The only answer was the pouring rain.  The golden man didn't speak.



``Wondered if I would see you here,'' Kevin continued.  ``Been a long time.  I'd nearly convinced myself I'd imagined you.  That old dog over there, he wasn't even born when I left, and he's on his last legs now.  Twelve years old.''



The golden man only stared.



Kevin turned away from the superhero.  Walking briskly, he caught up with Lisette's umbrella, picked it up and shook off the collected water.  He handed the umbrella to her.



``Scion,'' she whispered.



``No,'' Kevin said.  ``That was never his name.''



``I don't understand.''



``Come closer.''



She hesitated, but approached until she was a short distance from the golden man.  The pupil-less eyes had never left Kevin.



``I said I was the most powerful man in the world.  Wasn't lying,'' Kevin said.  ``See?''



The golden man didn't react.



``You control him?''  Lisette asked.



``No.  Not really.  Yes.  Not like you're thinking.''



``I don't understand.''



``Time was, this golden man spent his time wandering, floating here and there, observing but never doing anything.  In a daze.  Naked as the day he was born.  Everyone had different ideas on who he was.  Some thought he might be an angel, others thought he was a \emph{fallen} angel, and still more thought there were scientific explanations.  Only thing they ever agreed on was that he looked sad.''



``He does.'' Lisette was staring, but the golden man was only looking at Kevin.



``He doesn't,'' Kevin said.  ``Don't buy it.  He doesn't \emph{look} anything.  That expression never changes.  But whatever's underneath, that's what's giving you that feeling.  He looks sad because he \emph{is} sad.  Except you take out the `looks' part of it.''



``That doesn't make sense.''



``He bloody well flies!  And fights a giant continent-shattering lizard with golden laser beams!  Nothing about him makes any sense!''



The golden man turned his eyes away from the pair, examining one of the recently planted trees.  His eyes fixated on a leaf.



``What's he doing?''



``Getting around to that.  Was pure chance, but he stopped somewhere near here, dead of night.  Happened around the time I was still new to this life, when I was still feeling so sorry for myself I couldn't look anyone in the eyes.  I saw him, realized he was this same golden man I'd heard about on the news.  I was mad with depression, ran up to him and pounded my hands on his chest, yelled at him, swore, called him every name in the book.''



``Why?''



``Because he dared to be more miserable than me.  Or because people were putting all these hopes on him and he wasn't doing a fucking thing other than being some world-wandering nobody who happened to be able to fly.  Don't know.  A lot of it was me shouting at myself.  I said something about not being miserable, not being a waste, and maybe if he helped in a soup kitchen or something he'd feel better about himself.''



``A soup kitchen?''



``I didn't \emph{really} expect him to go work in a soup kitchen.  \emph{I} eventually did, but that's beside the point.  I told him to go \emph{do }something, go help people.  And he did.  Has been since.''



``Just like that?''



``Look at him.  There's nothing in there.  Whatever happened to him, whatever made him this way, it broke the man.  Broke his mind.  Might be why he was wandering.  Looking for answers, trying to figure out what's going on.''



The golden man continued staring at the leaves.



``He doesn't get offended?'' Lisette asked.  ``When you talk about him like he can't understand?''



``He understands.  He hears.  But I've never heard him speak.  Barely ever get him to look at me while I'm talking.  Doesn't show emotion, maybe doesn't understand it.''



``It's almost like he's autistic,'' Lisette said.



``How's that?''  Kevin asked.



``Too connected,'' Lisette said.  ``Too much in the way of stimuli, drowning everything out.''



``Enhanced hearing, hearing the whole city at once?''



``Maybe.  Or maybe he senses things we don't,'' she said.  ``The most powerful person in the world, and looking at him now, he's like a child.''



``Yeah, and unless something's changed,'' Kevin said, ``The only person he listens to is me.  He'd come when I was alone, when the weather was bad or in the dead of night, and however he comes, nobody ever followed him here.''



``They can't follow him with cameras or satellite, I heard.  Have to rely on eye witnesses and global communication to track him.''



``Oh.  Might be it,'' Kevin said.  ``Surprised he came with you here.  I thought- I almost thought he wouldn't, because I had you along.  It made me feel better.''



``Why?  Why avoid him?''



Kevin didn't take his eyes off the golden man.  ``He scares me.  He chose \emph{me} to listen to, of all people.  I'm the most powerful person in the world, just because of \emph{that}.  Because I can tell the strongest, most \emph{capable} man in the world what to do.''



``And you ran?''



``It took me a while to realize what I'd set in motion.  I started hearing about him.  Word on the street, newspapers, radio.  The golden man saves a small island from disaster.  The golden man interrupts a burgeoning war.  But it wasn't until that \emph{damned }clip began playing on the news that I realized what I'd gotten into.''



``I don't understand.''



``He'd visit regular, right?  Stop by, like he was checking if I had anything else to say.  Maybe I'd tell him to be more gentle with people when saving them from a car crash, or after that horned bastard came climbing out of the ground and the golden man flew right past it to visit me, I told him he needed to \emph{help} next time, to fight that monster and anything like it.  But sometimes I didn't have anything to say, and it's not like he obeys my every instruction down to the last detail, so sometimes he'd hang out here at half past four in the goddamn morning, and I couldn't get rid of him, so I'd just \emph{talk}.''



``Talk?''



``About whatever.  A book I'd gotten my hands on.  Current events.  The generosity of strangers.  Or I'd fix him up some clothes so he looked decent and talk about the clothes.''



He fell silent, watching the golden man.



``What happened?''



``He never responded, barely ever paid attention when I opened my mouth to ramble about whatever.  But he was following the general orders I gave him.  Help people, do this more, do that less.  But I'm in the middle of talking to him about my childhood, about home, when he latches on something.  Head turns, eye contact.  Scares the shit out of me.  I go over it all over again, but it was five in the bloody morning and I couldn't remember exactly what I'd said.  That is, I couldn't until three days later, I happen to be in the right time and place, and I see a television in a store playing this clip that's cropping up on the news.  The golden man says something for the first and last time.  Everyone seems to think he said Scion, and they latch onto it.  They're wrong, but it \emph{sticks}, and the word appears on t-shirts and in music and people are talking about it \emph{here, }where I live.  All because of one thing I said in some ramble of mine, the whole world changes.''



``That's what scared you?''



``It was the wake up call.  Stupid, isn't it?  Trivial.''



``No.  Nothing's trivial when you're talking about \emph{him}.''



The golden man had turned his eyes towards the river, his back to them.



``What did you say, if the word wasn't Scion?'' Lisette asked.



``Only realized later.  Was talking about home, religion and family.  Talking about a memory from my childhood.  Don't even remember it that well, now.  But the word he paid attention to was Zion.''



``That's Hebrew, isn't it?''



Kevin nodded.  ``Don't know.  Don't know the language, it was something to do with a cousin of mine getting in trouble when we were thirteen.  Don't know why he fixated on it.  But he did, and around the same time that clip started playing, they were talking about the things he'd done.  How he was still the most powerful person out there.  It's \emph{terrifying, }because all that power was at my command, mine to order around.  Because a filthy, do-nothing loser like me can change the world with a word.''



``You're not a loser.  You told him to help people.''



Kevin nodded grimly.



Her expression changed.  ``You're not going to change that, are you?''



He shook his head.  ``Golden man!''



The golden man floated around to face him square-on.



``I've screwed up, waiting so long to talk to you.  But I'm here now and there's two things we got to discuss.''



There was no response.  Only the motionless stare.



``This is a hard one, because I \emph{really} want to be wrong, here.  If this works, then it means my stupidity and my cowardice cost people big.  Means I could have fixed something much sooner.  Was only about the spring before last, I got a chance to use that newfangled internet.  Took some time to learn, but I read up on you.  Saw video of how you were fighting\ldots''



``Kevin?'' Lisette asked.



``Those Endbringer motherfuckers.  I told you that you need to stop them, that you need to fight and protect people.  And you have been.''



He clenched his hands, stared down at the ground, ``And god help me, maybe I wasn't specific enough.  Maybe I didn't realize you'd interpret me literally.  We need you to \emph{kill} the things.  Destroy every last trace of them, throw them into space.  Don't know.  But fight to kill, don't just\ldots God, I hope I'm wrong, that I'm remembering the words I chose all wrong, and that you didn't hear my suggestion and take it to mean you should fight \emph{for fighting's sake}, or fight to stop them, but not to stop them \emph{for good}.  You understand?  Don't just stop them from doing what they were doing.  Stop them \emph{permanently}.''



The golden man hovered in place, so still it looked like he was frozen in time, standing in the air.



``My god, golden man, I'm praying you understand.  Took me a year to get up the courage to do this, because I was afraid of this.  If that was the problem, and you kill one of those bastards, then I just- I just saved countless people, and the blood of every person they've killed in the meantime is on my hands.''



``Kevin,'' Lisette spoke, her voice quiet.  Her hands settled on his shoulders.



He ignored her, ``The other important topic?  I've run out of time.  Middle aged, and my liver's done in.  Never really drank, because I had to feed that dog over there.  Never did any drugs, besides smoking fags.  But I got the hepatitis somehow.  Bad blood in a hospital, or someone else's infected blood got mingled with mine on a night some kids decided to pick on a homeless man and I fought back.  Running into you the way I did, golden man, and having you stop to listen to me?  That was a one in a gazillion chance.  Getting this disease was another, might be.  Meeting you was the best and scariest part of my life, maybe it's the same with the disease, a blessing in disguise.  Maybe it was, aside from this young lady's help, the only reason I was able to find the \emph{balls} to come here.''



The rain wasn't as violent or as heavy as it had been.  It made for an audible change in the patter of water on stone and water on water.



Kevin sighed.  ``I'm here to get my affairs in order, and you're most important after Duke.  I want you to keep doing what you were doing.  Help people.  Try to communicate with the good guys more.  I told you to do that before and you didn't listen, but you should.  And if there's a problem, if you need someone to listen to, someone to visit from time to time, look for this young lady.  Lisette.  Because she's good people.  She's a better person than I am.  Braver.  \emph{Has} to be braver, if she's stopping to talk to a homeless motherfucker like me, following him someplace.''



``No,'' Lisette said, ``I couldn't.''



``Shitty thing for me to be doing,'' Kevin said, turning to look over his shoulder at her.  ``This burden.  But I somehow feel better about this than sending him to go obey you than telling him to go listen to and obey the Suits, or the Protectorate, or Red Gauntlet, or whoever.  You think about it, figure out what you need to, decide what he needs to be told.''



``You think he will?  He'll come to me?''  Lisette asked, her eyes were wide.



``Don't know, but I think he might.  Don't know why he picked \emph{me} to listen to, but he did.  I could've reminded him of someone he used to know.  Or he just up and decided we were friends, maybe.  With luck, he can be your friend too.''  Kevin sighed, ``You two got it?  You're partners now.''



Lisette couldn't bring herself to speak.  The golden man didn't respond either, didn't even move to glance at Lisette.



The golden man hovered in place for long, silent seconds, and then took off, faster than the eye could see.  Only a golden trail of light was left in his wake, quickly fading.



In mere seconds, Scion was gone.



``We have to tell someone,'' Lisette said.



``You can try.  They'll look at you the way you looked at me.  Like you've lost your mind.''



``But- but\ldots''



``Yeah,'' Kevin said.  ``Not so easy, is it?  Maybe if you're lucky, he'll show up when others are around, and they'll believe you when you talk about it.''



He sighed.  ``Come on, Duke.''



Lisette didn't resist as he grabbed Duke's leash.  Kevin started walking away.



``I don't understand!'' Lisette called after him.



Kevin didn't turn around or stop walking as he raised his voice to respond over the sound of the pouring rain.  ``Good deal, isn't it?  Ten pounds to become the most powerful person in the world.''





