





``Water torture,'' Justin said.  ``It's what the C.I.A. uses.''



``No, please.''



Justin shook his head.  ``What good is begging going to do?  There's hardly a point to torture if you \emph{want} it.''



``The victim can aspirate water during water torture,'' Dorothy commented, as though she were commenting on paint shades.  ``But I could have been doing it wrong.''



``Burning, then.  Start on the back, chest and stomach, work our way to the extremities.  They say a burn hurts worse than any other pain, inch for inch,'' Justin said.  ``By the time we work our way to the face, the armpits, or the soles of the feet\ldots''



``Oh god.''



``Scarring,'' Geoff said, looking up from his newspaper.  ``Chance of infection.  He'd be facing as much risk as he would with the water torture.  It might even be harder to treat.  Harder to explain if we had to go to a doctor.''



``Razors?''  Justin suggested.



``Razors could work,'' Dorothy said.  ``I'm good with a razor.''



``Hear that?'' Justin asked.  ``She's good with a razor.''



``Please.  There has to be another way.''



``There are a \emph{number} of other ways,'' Dorothy said.  ``Tearing out your teeth, fingernails and toenails is one.  Castration, force feeding, breaking bones, rats, flaying\ldots''



``I meant besides torture.''



``Psychological methods,'' Justin suggested.



``Isolation,'' Dorothy offered.  ``Sensory deprivation, intoxicants.  Would you like cream in your coffee, Geoff?''



``No thank you, dear.''



``The bacon is done.  Why don't you two come and eat?''  Dorothy offered.



Justin sighed. ``Come, Theo.''



The boy gave them wary looks as he stood from the armchair and crossed the length of their hotel room.  Dorothy had laid out a veritable feast: bacon, eggs, english muffins, toast, french toast, a bowl of strawberries, a bowl of blueberries, and a bowl of fruit salad.  There was orange juice and pots of both coffee and tea.  She was just setting down a plate of bacon, leaving barely enough room for anyone's plates.



It would have been too much for \emph{eight} people to eat, but she didn't seem to realize that.  She smiled as Justin ushered Theo to the table and sat down.  Her clothes were more fit for a job interview than for a fugitive, with a knee-length dress, heels, earrings and makeup.  Geoff, like his wife, was too well dressed for the occasion, wearing a button-up shirt beneath a tan blazer, his hair oiled and combed back neatly.



\emph{They can't act}, Justin thought.  \emph{They follow their routines like bad actors following a script.  A housewife preparing a meal for her family, the husband at the table.}



He'd known that the pair started every day with the same routine, like clockwork.  Wake, don bathrobe, and collect a newspaper.  Geoff would step into the shower as Dorothy stepped out, and she would be done grooming by the time he was through.  Once they were both dressed, they'd head to the kitchen, and Geoff would read the paper while Dorothy cooked.



But always, the details would be off.  Things any ordinary person would take for granted were forgotten or exaggerated.  Dorothy inevitably prepared too much, because it was \emph{harder} for her to consider how hungry everyone was and adjust accordingly.  Only two days ago, Justin had noted that Geoff would take a few minutes to read the front page of the paper, turn the page, and stop.



Now he couldn't help but notice.  It was the same thing every day.  For the twenty or thirty minutes it took Dorothy to put everything together and set it on the table, Geoff would stare at the second and third pages of the newspaper.



Justin had asked about the headlines and the articles.  Geoff never remembered, because he wasn't \emph{reading}.  He \emph{could} read, but he didn't. He spent nearly forty minutes in total, every day, like clockwork, doing little more than staring into space, \emph{pretending} to read.



\emph{Put the paper away, it's time to eat, }Justin thought.  \emph{Yes dear.  Mmm.  Smells delicious.}



``Put the paper away, it's time to eat,'' Dorothy said.  She was holding the coffee pot, stepped behind Geoff, putting a hand on his shoulder, and bent down to kiss him on the top of his head.  Automatic, without affection.



``Yes, dear.  '' Geoff said, smiling up at his wife.  ``Mmm.  Smells delicious.''



\emph{Jesus fuck, they scare me}, Justin thought.  But he plastered a fake smile of his own onto his face, grabbed one of the oven-warmed plates and served himself.  Theo did much the same at the other side of the table, minus the smile.



Kayden emerged from one of the bedrooms, her hair still tangled from sleep, wearing a bathrobe.  Mousy, shorter than average, looking exceedingly \emph{human}, she was Dorothy Schmidt's antithesis.



``Aster slept well last night,'' Justin commented.  ``Didn't hear her crying.''



``She slept through the night.  We just have to maintain a routine as we keep moving,'' Kayden said.



``We were just discussing ways to force Theo's trigger event.''



``It'll come on its own,'' she said.  ``We have two years.''



``One year and eleven months,'' Theo said.



Kayden glanced at him but didn't respond.



``It should have happened already,'' Justin pointed out.  ``It's easier for children with inherited powers, and Theo's the son of Kaiser, who's the son of \emph{Allfather}.  Third generation.''



``Maybe I didn't get powers,'' Theo said, not looking up from his plate.



``Or maybe you've lived a sheltered enough life that you haven't had a reason to trigger,'' Justin retorted.



``I don't want to get tortured.  Physically \emph{or} psychologically.  There has to be another way.''



``Torture?'' Kayden asked.



``It's one line of thought,'' Justin said, trying to mask his annoyance.  He'd purposefully brought it up while Kayden was out of the room.  ``We were trying to think of methods that wouldn't leave him unable to fight Jack when the time came.''



``No torture.  Theo's right.  We can find another way.''



Justin frowned, ``Every day we wait is a day we don't have for training his abilities, and he'll need all of the training he can get.''



``Because I have to fight the Slaughterhouse Nine and Jack Slash.  And he'll kill a thousand people if I don't,'' Theo said.  ``Me and Aster too.''



Justin glanced at the boy, saw the white-knuckle grip he had on his knife and fork, looked at Kayden, who had french toast speared on her fork but wasn't raising it to her mouth.  She stared off into space as the maple syrup slowly dripped down to the plate below.



\emph{She doesn't know what to do any more than we do}.



``You come from a good pedigree,'' Justin commented.  ``Kaiser was strong enough to rule over the better part of Brockton Bay, as Allfather did before him.''



``Which doesn't do us any good if I don't get powers,'' Theo mumbled.



``If worst comes to worst,'' Kayden said, ``\emph{We} fight the Slaughterhouse Nine.  Night, Fog, Crusader and I.  Okay?''



Justin frowned, but he didn't speak.



Theo voiced half the doubts that Justin was keeping silent, ``You didn't fight them last time.  I'm not saying you were wrong to leave, but-''



``But we didn't fight them then.  You're right,'' Kayden said.  ``I'd hoped the others would stop them.  The heroes, the Undersiders, Hookwolf\ldots''



``And they didn't,'' Justin said.  ``Which means we have to assume Jack's going to follow through.  That gives us a time limit.  Theo needs powers, he needs \emph{training}, we need to find the Nine, and we need to stop them.  What if we went to the \emph{Gesellschaft}?''



Kayden glanced at the other two who were sitting at the table.  Dorothy and Geoff.  Neither of the two had reacted to the name of the organization that had created them.  Or, at least, they hadn't reacted \emph{outwardly}.



``I'm more concerned that they'd \emph{help} the Slaughterhouse Nine if it meant killing a thousand Americans,'' she said.  ``And I'm not sure I want Theo to recieve the kind of power they offer.''



``If we contacted them through Krieg\ldots''  Justin trailed off.



``What?'' Kayden asked.  She let her knife and fork drop to her plate with a loud clatter.  ``You think they'd give us assistance with no strings attached?  That we could call in a favor with Krieg and they'd give Theo powers, without the follow-up attention?''



``No.  No, I suppose not.''



``They turn people into\emph{ weapons},'' Kayden said.  ``Then they decide where those weapons are best positioned, for the \emph{cause}.  There's two good reasons why they wouldn't have given fresh orders to Night and Fog since the Empire collapsed.  Either they can't get in touch with us-''



``I somehow doubt that.''



``Or Night and Fog are forgotten.  Presumed dead or ignored,'' Kayden finished.  ``In which case we don't want to remind them that we're still around.''



``I somehow doubt \emph{that}, as well,'' Justin said.  ``They have to know we're alive.''



``Then what?  Why leave these two in my care?''



``Because it serves their agenda,'' Justin answered.  He finished off his plate, spooned some blueberries onto the side, and poured himself some orange juice.



``What agenda?''



``The Empire fell.  The Chosen fell.  Only Kayden Anders and her \emph{Pure} remain.  If they hope to retain any foothold in the Americas, it'll be through you.''



``I don't \emph{want} to give them a foothold in the Americas.''



``By the sole fact that you \emph{exist}, you're giving it to them.  Your reputation, your success, it gives the Gesellschaft the opportunity to say, their cause is being furthered in the West.  Even if your goals and theirs are only aligned in abstract.  So they leave Night and Fog in your care, because it keeps you dangerous, it helps ensure your success, and maybe because it gives them a way to strike at you if they decide you're a danger to the cause.''



Kayden glanced at Dorothy, studying Night's civilian appearance.



``More coffee?'' Dorothy asked, smiling.



``God, yes,'' Kayden muttered.  She held out her cup for a refill.



``What about you?'' Theo asked.



Justin turned to look at the boy.  ``Who?  Me?''



``Where do \emph{you} stand, with \emph{the cause}?''  Theo asked.  Justin didn't miss the inflection at the end.



``I'm a simple man,'' Justin said, smiling.  ``I like steak and potatoes.  I like a good fight, a serious game of baseball or football.  \emph{American} football.  I like a good woman's company-''



Kayden cleared her throat.  When Justin met her eyes, she was glaring at him.  Not jealousy, more of a mother bear protecting her cub.



Justin smiled a little, more with one side of his mouth than the other.  ``-And I believe that \emph{they} are fucking things up, out there.  And the rest of the world's letting them.''



``People with different colored skin.''



``People with \emph{differences},'' Justin said.  ``Faggots, gimps, mongoloids.  Kaiser \emph{got} that.  I talked to him one on one, and he had the right ideas.  He \emph{got} that America is \emph{ours}, that they're polluting it over time, letting these people in.  But he was too focused on the big picture, and he was working with the Gesellschaft, which was \emph{way} too big picture for my tastes.  Still, birds of a feather.  I worked under him because I wasn't about to find others elsewhere, and I didn't feel like going it alone.  Then he introduced me to Purity.''



Theo glanced at his onetime stepmother.



``And I think we're more in sync, Kayden and I,'' Justin said.  ``If Kaiser was the visionary, the guy on top, the guy with the dream, working to achieve something over decades, then Purity's the detective working the streets.  And that's the kind of simple thinking I can get behind.''



``So you don't support the Gesellschaft?''  Theo asked.



``I can't support what I don't understand,'' Justin said.  ``And what I \emph{do} understand is that we need to give you your trigger event before it's too late.  Because Jack and his gang of psychopaths are the sort of freaks I can't stand, and I'll be \emph{fucked} if we let him beat you on this count.  \emph{They} don't get to beat \emph{us}, and you're one of us.''



Theo drew in a deep breath, as if he was going to say something, and then heaved it out as a sigh, slow and heavy.



``Whether you like it or not,'' Justin added, just under his breath.



Theo glanced at him.  He hadn't missed the comment.



At a normal volume, Justin said, ``You're vetoing the torture, where we'd be trying to get him to a trigger state in a safe, \emph{controlled} environment.  We need another game plan.''



Kayden sighed.  ``For now?  We'll let Dorothy clean up.  Have you two done your morning sparring?''



Justin shook his head.



``Give Theo some training while I shower, then you two can wash up.  Get dressed to go out.  I have one idea regarding Theo's trigger event.''



Justin stood with a plate in hand, but Dorothy was already walking around the table, her heels clicking on the tile.  She took the plate from him, smiling.



``Come on, then,'' Justin urged the boy.  ``Let's see how much of it's sinking in.''



``Not much,'' Theo said.



``Probably not,'' Justin replied.  He reached for his power and stepped out of his body, a spiritual mitosis.  A ghostly image of himself, wearing the same clothes, crossed the `living room' of the space the hotel had given them.  He created two more replicas of himself, one walking until its legs were sticking through the couch.



``Four against one?''  Theo asked.



``You think the Nine are going to play fair?  Now, do you remember priority one?''



``Self defense.''



``Protection comes first, always.  The core of any martial art or self defense.  Perception's second.  Know what's going on, because it'll help you protect yourself, and it'll help you identify the right moment to strike.  Arms up.  Let's see your stance.''



Theo raised his arms in the ready position, positioned his feet further apart.



Justin looked the boy over.  He'd lost a little weight, though he wouldn't look much skinnier if he kept exercising like he was.  He'd put on muscle, and look just as bulky, at least for a while.



But that stance\ldots



Justin suppressed a sigh.  \emph{Those one thousand people are fucked.}



\sectionbreak



``Harvard,'' Justin said.



``This way,'' Kayden said.  She had Aster in a harness, the baby's head resting against her chest.



``You know your way around \emph{Harvard}?  Color me impressed.''



``I looked it up online.  This way.  I'd rather not spend too much time in public.''



Justin noted the crowd of older teenagers and twenty-somethings.  It was summer, but the school wasn't empty.  With the warmth of summer, the students were wearing shorts and short sleeves, as well as short dresses.  Justin smiled at a group of girls as they passed by.  One of them looked over her shoulder at him, gave him a glance that roved from head to toe and back up again.



``Justin,'' Kayden said, raising her voice.



``Coming,'' he said.  \emph{Damn}.



They made their way across the campus.  Dorothy and Geoff had stayed behind, leaving Kayden, Justin and Theo to carry out the errand with Aster in tow.



They reached a tower, built to match the other buildings of the campus.  Justin held the door for Kayden and Theo, pausing to note the lettering across the entrance: `Dept. Parahuman Studies'.



Fitting.  Kayden's plan was clear, now.



They entered the elevator, and Kayden checked a slip of paper, hit the button for the ninth floor.  She tucked it into a pocket behind Aster's back, then kissed her sleeping daughter on the forehead as the doors closed.



``We should get in and out fast,'' Justin commented.



Kayden pursed her lips.



``Always have to consider that someone made us, and that they're calling the authorities.''



``I know,'' she said.



``Fuck Coil,'' Justin snarled.



Kayden glared at him, and her eyes and hair both glowed with a trace of light.  Some free strands of hair lifted as the light touched them, as if they were buoyant, or as if Kayden was underwater and slowly sinking.  ``Watch your language around Aster.''



``She doesn't understand.''



``But she \emph{will}, one day.  Get in the habit now.''



Justin sighed.  ``Will do.  We going in hard or soft?''



``You could rephrase that.  But this is a soft entry.''



``Right.''



They departed the elevator as it reached the ninth floor.  Kayden double checked the slip of paper, and they began the process of figuring out where the room was.  It wasn't intuitive, as the rooms didn't seem to be numbered sequentially.



They stopped at one door that was labeled `914', with a nameplate below reading `Dr. Wysocki'.



``What the hell kind of name is Wysocki?  Polack?''



``He's one of the top researchers on Parahumans,'' Kayden said.  ``The best in the Massachusetts area.''



``You're the boss, and it's your call,'' Justin said, shrugging.  ``Just saying I pointed it out in advance.''



``What difference is it going to make?'' Theo asked.  ``Doesn't make any difference to his ability to do his job.''



``So cute,'' Justin said.  He gave Theo a pat on the cheek, and the boy pushed his hand away in irritation.



Kayden knocked, and the door swung partially open.



A young man, no older than twenty-five, hopped out of his swivel chair, pulling earbuds from his ears.  ``Ah.  Hi?''



``We had a few questions,'' Kayden said.



``I've never had a student bring their family before.''



``We're not students,'' Kayden said.  She strode into the room, and Justin gave Theo a push on the shoulder to prod him forward.  When everyone was inside, he closed the door and stood with his back to it.



``Huh.  I thought I recognized you, would have been from class,'' the man said.



``We're not students,'' Justin echoed Kayden's words.  His tone didn't have the intimidating effect he'd hoped for.  The young man's forehead was wrinkled in concerns of a different sort.



``You're not here for the office hours?  Figures.  I sit around for three hours twice a week, five straight weeks, someone \emph{finally} shows and they aren't a student.''



``You're Wysocki?'' Justin asked.



``No,'' the young man gave him a funny look.  ``You're \emph{really} not students.  I'm the T.A.  Filling in while he's at an event.  Peter Gosley.''



He extended a hand, but nobody accepted it.



``Fuck,'' Justin said.  ``\emph{This} is a waste of time.''



``If you have questions\ldots'' Peter trailed off, letting his hand drop.



``Trigger events,'' Theo said, his voice quiet.



Peter's eyes fell on the boy, widening slightly.  ``You have powers?  You just got them?''



``I need them,'' Theo answered.



Peter gave them a funny look.  ``I\ldots I'm not sure I understand.''



``Tell us what you know about trigger events, and perhaps we'll explain,'' Kayden said.



``I\ldots that's a broad field.  What do you want to know?''



``How to have one,'' Theo said.



``Trust me, there isn't a single government out there that isn't \emph{trying} to pull it off.  None have had much success with the various methods they've tried.  Not to the point that anyone else has been able to copy their methodology.  If anyone \emph{was} succeeding, it'd be off the radar.  Maybe the Protectorate.''



``What methods have they tried?'' Justin asked.  ``The governments.''



``Anything?  Everything.  Drug induced panic attacks.  Kidnappings.  Torture.  Some with willing participants, some even with participants in the dark.  The Queensland Trials-``



``Stop,'' Kayden said.  Peter stopped.  ``Participants in the dark?  And nothing worked?''



``It \emph{sometimes} worked, a lot of stuff \emph{sometimes} worked.  The problem is, the act of getting a trigger event tends to throw a controlled situation into disarray.  A government or organization pours hundreds of man hours and half a million dollars into identifying people who \emph{might} be parahumans, by whatever metric they're using, tracking them, covertly acquiring them, and inducing the parahuman state\ldots and it'd work one in two hundred times.  Half of \emph{those} times, they'd wind up with a parahuman in an agitated state and things would fall apart.  So a lot of the successes end up being failures of a diffferent sort.''



``But they haven't found a consistent way of getting people to trigger?'' Kayden asked.



``No.  Fact is, it's \emph{harder} when you're \emph{trying }to provoke a trigger event.  Even if the participant doesn't know you're trying it.''



``Why?''  Kayden asked.



Peter shrugged.  ``There's theories.  There's the specific trigger theory, which suggest that each individual demands a particular kind of trigger event, so any attempts to force it are essentially attempting the wrong form of trigger.  There's the specific \emph{circumstance} theory, which is different, because it suggests that it's not just a particular \emph{type }of trigger that's demanded, but the specific time or event.''



``You're saying it's predestined,'' Justin said.



``\emph{Some} scholars say it's predestined.  I don't.  Um.  Other theories\ldots there's intelligent intervention.''



``Phrase it in American fucking English,'' Justin said.



``There's no need for rudeness,'' Peter said.  He adjusted his glasses and frowned at Justin.



``Please phrase it in American fucking English,'' Justin clarified.



``\emph{Please} explain,'' Kayden said, shooting Justin a look.



``It means there's someone or something that's deciding who gets powers and when.  There's subtheories\ldots Aesthetic analogue, where they're saying the powers tend to relate to the trigger event somehow, so obviously someone's doing it on purpose.  Uh.  Intelligent \emph{powers}, where they say \emph{the powers }are sentient and they're making the call on their own.  Ties into other areas of study, and it's a favorite of mine.  There's the-``



``This isn't helping us,'' Justin cut in.



``Quiet.  Everything helps,'' Kayden said.



``We're short on time.''



Peter gave him a funny look.  ``Look, I'm not fully understanding what you're getting at.  It's great that people are interested in this stuff, but this notion you have that, because your son wants powers, you're somehow going to give him a trigger event?  That's a little freaky, it's not really possible.  And, uh, it's borderline abuse, if not \emph{actual} abuse.''



``It's a complicated situation,'' Kayden said.  ``What else can you tell us about trigger events?  Beyond theories?''



``The manner of trigger event seems to impact the powers.  That's frosh level stuff.  Physical pain, physical danger; physical powers.  Mental pain, mental crisis?  Mentally-driven powers.''



Justin frowned.  \emph{And being the brother of a dying, half-blind, deaf retard of a girl who got all the attention?  All of the gifts, the money?  Being made to get surgery for her sake, give up years of my lifespan so she might live?  Getting caught pulling the plug, only for it to do little more than set alarms going?}



Was his power really a mental power?  He'd always considered it more physical.



He looked at Kayden, studied her concerned expression.



Peter was still talking, responding to something Kayden had said.  ``Drugs tend to create \emph{conditional} powers.  It's not hard and fast, but you get situations where the power is directly linked to one's physical, mental or emotional state.  We think it's because the power works off a template it builds as the powers first manifest.  If someone is riding an emotional high as they trigger, their powers will always be looking for a similarly excited state to operate at peak efficiency, often an emotion or drugs.  When people were caught trying to fabricate trigger events, sometimes they were intending to \emph{use} this so the subject would be more easily controlled.''



``I wonder if lack of food and water could create similarly conditional powers,'' Kayden commented.



``I'm\ldots are you talking about starving him?''  Peter's eyes were wide now.



``Not at all.  I'm\ldots speculating.''



Justin could follow her train of thought.  He'd heard the story through the Empire's grapevine, once.  A sixteen year old girl, driving for the first time, down a side road, getting in an accident where her car rolled off the road, out of sight of anyone passing by.  Trapped\ldots starving, dying of thirst.



Getting powers that fed off and required other resources.  Light.



He glanced at her, and she offered him a curt nod.  Without speaking, they'd come to a mutual agreement that this `Peter' knew what he was talking about.



``What's the impact of being the child of a parahuman?'' she asked.



``Um.  I \emph{love} that you're interested, and yeah, I wasn't really doing anything, but maybe if you have this many questions, you should \emph{take a class}?''



``He's the son of a parahuman,'' Kayden said, pointing at Theo.



\emph{Cat's out of the bag now.}



``No kidding?  Wow.  Who?''



``Kaiser,'' Kayden said.



Peter's eyes widened as he looked at Theo.  Then something seemed to click, and he looked up at Kayden and Justin with a note of alarm in his expression.



``Yeah,'' Justin said.  ``Smart man, and you're only figuring it out now?''



``I saw the stuff on the news.  \emph{Thought} I recognized you.  Purity and\ldots''



``Crusader.  So maybe now you understand we're serious.  And how we're \emph{not} interested in taking a class,'' Justin said.



``If he's Kaiser's son, and Kaiser's Allfather's son\ldots he's third generation.''



``And he doesn't have powers,'' Kayden said.  ``It's crucial that we fix that.''



``I\ldots I don't really know.  It's supposed to be ten times easier to get powers if you're second generation.  But we don't have research on third generations yet.  It's only pretty recently that we had the first third-generation cape \emph{on record}.  The baby in Toronto.''



``Didn't hear about that,'' Kayden said.  She frowned.  ``A \emph{baby}?''



Peter's eyes fell on Aster.  ``Oh.  Wow.  Is she third generation too?''



``Pay attention,'' Justin said.



``The\ldots yeah.  Each successive generation seems to produce \emph{younger} capes, by lowering the barrier to entry, the severity of the requisite trigger event.''



``So why haven't I triggered?''  Theo asked.



``I don't know.  There's a \emph{lot} we don't know.   Maybe\ldots maybe you don't have powers.''



``I \emph{have} to.''



``It's a question of luck.''



``You don't understand.  If I don't get powers, a \emph{lot} of people will die.''



``I'm not sure I follow.''



``It doesn't matter,'' Justin said.  ``Give us all the information you have.  Every way you've heard about people trying to trigger, and how well they worked.''



``That's a six month lecture series unto itself!''



``Talk fast,'' Justin said.



``Um.  There's meditation.  Either to tap into your deeper psyche or to tear down the walls between yourself and your worst fears.  There's theories that the powers themselves are intelligent, and they're worked into the host's head, before or after the trigger event.  Sometimes the meditation's related to that, but it's usually people trying to have a second trigger event.''



``That's not relevant to the boy, is it?'' Justin asked.



``The research is related!  There's a lot of research into \emph{second} trigger events because it's a lot easier to find willing parahumans than it is to find \emph{potential} parahumans.  The methods that people try tend to be similar, too.  It's just\ldots a lot of the time, they fail for opposite reasons.''



``Opposite?''  Kayden asked.



``It's not confirmed, it's just an idea, but the idea the powers are sentient?  Well, either the second trigger event opens up communication, frees the powers to act on their own more, or if you don't buy that stuff, it breaks down the mental barriers between the altered part of the brain that controls the powers and the part that doesn't.  At least, that's going by the patterns we've seen.  Except\ldots well, we think sometimes the reason people can't have a second trigger event is because they've \emph{already had one}.  You can't really distinguish a single trigger event from having two in quick succession.''



``Like a multiple orgasm,'' Justin commented.  Kayden glared at him.



``More or less.  There's more parallels than that, but yeah.''



``Crusader is right, this isn't helping him,'' Kayden said.



``What kind of trigger events did Kaiser and Allfather have?''



Kayden and Justin exchanged glances.



``No idea,'' Kayden said, frowning.



Peter frowned.  ``That would have helped.  At least we know they both had similar powers.  Allfather could conjure iron weapons from the air immediately around himself, send them flying.  Kaiser could call metal out of any solid surface.  Both are the kind of powers you'd see from almost purely mental trauma.  If the trend continues\ldots''



He trailed off, leaving the sentence hanging.  Theo would probably require mental trauma to trigger.



``Hard to imagine Kaiser having mental trauma.  He seemed so confident,'' Kayden said.



``His dad was Allfather.  Not so hard to imagine,'' Justin replied, absently.  He thought of the college girls and stepped over to the window, curious if he'd be able to make out any from this high up.  He froze.



``Kayden,'' he said.



``What?''



``Cops.  And containment vans.''



``Someone made us?''  Kayden asked.



``And saw us enter the building,'' Justin finished.  ``They're surrounding us on the ground.''



``\emph{Shit!}''  Kayden swore.



Aster whimpered, then started crying.



\emph{Didn't you tell me to watch my language in front of Aster?}  Justin thought.



Theo was sitting in a swivel chair, hands clasped in his lap, his eyes watching Kayden, waiting for her cue.



Justin noted the tension of Theo's grip, the way he seemed to retreat into himself.  The fat little boy who was nothing like Kaiser.  Maybe he hadn't inherited powers at all because he wasn't his father's son.  If his mother had cheated on Kaiser, gave birth to this pudgy blob, it would explain why he didn't have powers.  It would mean he wasn't a \emph{second} generation cape, let alone a third.



``Hmm.''  Justin watched more PRT vans arrive.  They were spreading out, clearly anticipating Kayden's artillery-level attacks, and they had the damn foam-bead nets they used for dealing with fliers.  ``Theo, who's your mom?''



``Heith.''



Justin sighed.  Heith was Fenja and Menja's cousin and guardian, Kaiser's first wife, killed in a turf war with the Teeth, back in the old days of Brockton Bay.\emph{  }\emph{She has powers after all.}



Somehow, all of this would be easier if he could believe that Theo was illegitimate.



``Crusader,'' Kayden said, ``Can you stall them?  We have more questions.''



He nodded, shut his eyes, and drew on his power.



It was as simple as stepping forward while staying in the same place.  A ghostly phantom appeared, followed by another, and another.  One headed for the elevator shaft, while the other headed for the stairwell.  He directed the remainder to sink through the floor.



``What else can you tell us?  Something we can use,'' Kayden said.



``If the authorities are here, I don't know if I should say.''



``You should,'' Justin said.  ``Because we'll hurt you if you don't.''



``Don't,'' Theo said.



Justin gave the boy his best dispassionate look.



``He's been helpful,'' Theo said.



``He hasn't solved your problem,'' Justin said.  He was dimly aware of his other selves engaging with the enemy as they moved into the building.  One fought them in the stairwell, immune to any strike or bullet, yet fully capable of pushing a man down the stairs, into the people behind him, fully capable of strangling a man.



Peter shifted positions nervously.  His voice rose in pitch as he spoke, ``I don't know what you want.  I can't give you an answer because there \emph{aren't any!}``



``\emph{Think},'' Justin suggested.



``You expect me to do in five minutes what the best scholars in the world haven't figured out in \emph{thirty years}?''



``Well put,'' Justin said.  More clones were still splitting off, breaking away from himself to sink through the floor.  Some had moved beyond the building to attack the men who were manning the turrets on top of the van.  With luck, he and Kayden would be free to fly to safety with the children.



``This\ldots this is insane!  What am I supposed to tell you?  I've outlined some of the best theories we have!''



``If it helps,'' Justin said, leaning towards Peter, ``I'm going to kill you if I don't leave here satisfied.  Think about that.''



``Kayden,'' Theo said, ``You're not going to let him, are you?''



``Crusader,'' Kayden said.  ``Is that really necessary?''



``I can't even think straight under this pressure!'' Peter cried.



``I imagine you feel very similar to someone about to have a trigger event,'' Justin said.  ``Maybe that will inspire something or fill in the blanks for some half-baked idea you had once.''



``I don't\ldots There's isolation.''



``An isolation chamber?'' Justin asked.



Peter shook his head.  ``No.  More basic.  It's a common trend.  People who have trigger events, they don't usually have a good support system.  Their family, their friends, they tend to fail them, or be the cause of the problem.  I\ldots I wrote a paper a while back about how Masters tend to have loneliness as part of their trigger events, and how maybe that was why Masters tend to be villains.  Because you need support and social pressure to be more of a good guy.  My professor then, the guy who I work for now, Dr. Wysocki, he tore me to pieces.  Too many other parahumans have it as part of their history.  Isolation.  It wasn't enough to suggest a correlation.  He said you could call it a common theme for nearly all of the trigger events out there.''



Justin was in the middle of creating another ethereal copy of himself when he stopped.  It snapped back into place.  He thought back to something earlier in the day.



``Kayden, let's go.''



``What?''



``I've got our answer.  Let's go.''



``Are you sure?''



Justin nodded.



``To the roof?'' she asked.



``As fast as you can move with the baby.''



Kayden rose into the air, her hair and eyes lighting up.



``Come on, Theo,'' Justin said, ``I'll carry you.''



He spawned a ghostly replica as Kayden left the office.  Theo hesitated as the replica got closer.



``What's wrong?'' Justin asked.



``What he just said\ldots  You're going to leave me.  Isolate me.''



``Yeah,'' Justin said.  His ghost-self lunged, and Theo threw himself back with such force that he fell over in the chair.  The ghost was on him in a second, pinning him down to the floor with one hand around his throat.



``Don't.  You heard what he said.  If you force it, it won't happen,'' Theo protested, his voice barely above a wheeze with the hold the ghost had on his neck.



``I'm willing to take that chance.  In the worst case scenario, you're \emph{their} problem, not ours.  The heroes can look after you and figure out what to do with you.''



``Justin!  Crusader!''  Theo managed a strangled scream, but Justin was already in the doorway, not even pausing or hesitating at his words.  ``It won't work if you try to make it happen!''



Justin left Theo behind, stepped into the stairwell, noting a gap between the stairs that was big enough to fly between.  He created a clone and left it overlapping his body, using its flight to lift himself into the air.



Kayden hadn't flown for safety yet.  She was waiting on the rooftop, Aster writhing in the harness, screaming bitterly.



``Fly,'' he said.



``Where's Theo?''



``Would you believe me if I said he was coming?''



He could see her expression shift in time with the realization.  ``You didn't.''



``I did.  And you won't go back for him.''



``Like hell I won't.  He saved Aster when Jack was going to kill her, he might have saved \emph{me} in the process.  I owe him-``



``-And we're paying him back by leaving him.''



``No.  No, we aren't.''



``He's one of our own, kind of.  I get that.  But\ldots he was never going to help the cause.''



``The \emph{cause},'' Kayden spat the word.



``Purifying the world, cutting out the rot, becoming a symbol of better things.  It's not him.''



``He's my stepson.''



``And isn't that the problem?  Remember this morning, at breakfast?  He was worried he wouldn't get powers.  That he wouldn't be able to stop Jack.  And how did you respond?  You reassured him.  You told him \emph{we'd} fight the Nine if he couldn't.''



Kayden only glared, eyes shining with painful brightness.



``When you said that, part of me, I thought \emph{we didn't fight the Nine then, how could we two years from now?  }Theo said it outright.  He's sharper than he looks sometimes.  Sharper than he acts.  But here's the thing, at the same time, a part of me felt like I'd realized something, and it took me until now to get it sorted in my head.''



``What?''



``You're reassuring him, when that's the last thing we want.  When there's a crisis, he looks to you.  The most basic requirement for a trigger event is you get to a point where you can't \emph{go} anywhere.  Pushed to your limit and then pushed further.  He can't get there so long as \emph{we're} there as a safety net.  As a support system.''



``So we're supposed to abandon him?''



``We just did,'' Crusader said.  ``The authorities are just getting to the ninth floor now, my clones are letting 'em by.  By the time we got there, they'd have him secured, and they'd be ready to spray us with that foam.''



``You could use your power, disable them without any risk.''



``I could.  But I won't.''



Kayden flared with light, and for a second, he thought she was going to shoot him.



The blast of solid light didn't come.



Justin sighed, ``He'll be hurt, he'll be pissed, and he'll be alone.  They'll quiz him on us, get every detail they can, and if I know him at all, it'll tear him up, because he might not like us, but we're the closest thing he's got to family\ldots''



Kayden glanced toward the door.



``\ldotsAnd that's the best thing we can do for him right now,'' he finished.



``I never was the mom he needed,'' Kayden said.



``Well, it's too late now.''



She walked over to the roof's edge, peered down.  ``Any net launchers?''



``Nobody to aim them now.  Everyone's fighting my doubles.''



She glanced back toward the door, absently cooed for Aster to stop crying.



There was a flash of light.  By the time it cleared away, she was merely a glinting speck in the distance.



He glanced at the door, then flew after her.



\emph{Up to you and you alone now, boy}, he thought.





