





Dr. Jeremy Foster was woken by the sound of a distant gunshot.  He sat straight up in bed.



Another gunshot.



He reached over to his bedside table and found the remote.  A press of a button illuminated his bedroom.  He opened the drawer to grab the handheld radio and pressed the button.  ``Report.''



Silence.



``Captain Adams, report.''



It wasn't Captain Adams who responded.  It was a woman.  ``\emph{Stay put, doctor.  We'll be with you in a moment.}''



He was out of bed in a flash.  Remote in hand, he turned off the light and opened his bedroom door.



There were two figures in the hallway, cloaked in shadow, one large and broad, the other narrow.  The smaller one saw him and broke into a run.



He slammed the bedroom door and locked it in the same motion.  There was a crash as the figure threw himself against the door.  If the door were the usual wood chip and cheap cardboard, it might have broken, but Jeremy valued \emph{quality}, even with the things one normally didn't see.  His doors were solid wood.



The doorknob rattled as the doctor crossed his bedroom.  He reached for the underside of one shelf on his bookcase, pulled a pin, and then pulled the bookcase away from the wall.



The remote fit into a depression on the stainless steel door that sat behind the bookcase.  He made sure it was positioned correctly, then hit a button.  There was a click, and the door popped open a crack.  He had to use both hands to slide the door open.



The doorknob rattled again, then there was a heavier collision.  The bigger man had gotten close.



Safely inside, Jeremy pulled the bookcase tight against the wall, felt it click into place, and then shut the metal door of his panic room.



Monitors flickered on, showing his estate in shades of black and green.  At any given time, he had seven armed men patrolling the grounds and an eighth keeping an eye on the security cameras.  He could count seven fallen, including the man in the security office.   They lay prone on the ground, or slumped over the nearest surface.  One struggled weakly.



He picked up the phone.  There wasn't a dial tone.



The cell phone, then.  He opened a drawer and picked up the cell.  No service.  There was only static.  They had something to block it.



There was no such thing as `security'.  However much one invested in safes, in armed guards, in panic rooms and high stone walls, it only served to escalate a perpetual contest with the people who would try to circumvent those measures.  Raising the stakes.



Helpless, Jeremy watched the invaders making their way through his house.  He was already mentally calculating the potential losses.  Pieces of artwork worth tens of thousands, valuables not secured in the safes\ldots



The Magnes painting at the landing between the second and third floor, overlooking the ground floor foyer.  Jeremy winced at the realization.  He'd only picked it up two months ago.  The two million dollar price tag might have given him pause, but it was insured.  He'd bought all the furniture for foyer to complement the work, and now he'd have to find another painting to take its place and buy new furniture to match.



Except they were walking by the painting as though it weren't even there.



A part of him felt offended that they hadn't even stopped to admire it.  Philistines.



No.  There was a very good chance they were coming for \emph{him}.



One by one, they entered his bedroom.  It was a blind spot of sorts.  He'd wanted his privacy, so the only ways to turn on the security camera in the corner of the room would be to unlock or open the balcony doors, break the glass or input a particular code.



He stepped over to the computer, typed in the code.  Simonfoster19931996.



The screen flickered to life, but it wasn't his bedroom in the picture.  A field with four walls approximately where his bedroom walls had been, the six invaders waiting very patiently in the middle as walls stripped away to become tendrils, tendrils became vines and vines twisted together into treelike forms.



The window went quickly.  The `field' of knee-length grass rippled as the wind caught it.



The bookcase was slower to degrade.  Books were rendered into leaves, shelves into vines.  He watched the image on the camera with an increasing sense of dread, glanced at the door.



The screen went black.



``No, no, no, no,'' he said.



A crack appeared in the door.  Floor to ceiling.



He grabbed the handgun from the counter, double checked it was loaded.



Another crack crossed the door, horizontal, nearly six feet above the ground.



He disabled the safety.



With the third crack, the door fell into the panic room, slamming against the ground.  He fired into the opening of the doorway, and the acoustics of the metal-walled room made the shot far, far louder than it had any right to be.



There was nobody standing in the doorway.



He looked around.  The layout of the room wasn't set up for a firefight.  Especially not a firefight that involved parahumans.  He crouched, kept the gun pointed toward the door.



They didn't make a move. The floor of the panic room was being finely etched with markings that overlapped and wove into one another.  Where lines drew to a taper, points were curling up, strands slowly rising, dividing into finer growths and flaring at the top with the vague cat-tail like ends of wild grass.  He could see the clean-cut edges of the door curling, twisting into tendrils.  Some had teardrop shaped bulges on the end.



``Elle,'' he called out.  ``Labyrinth?''



All together, the bulges on the tendrils unfurled into tiny, metallic flowers, framing the doorway.



``She's having one of her bad days, doctor,'' the woman who had been on the other side of the radio called back.  ``She's not feeling very talkative as a result.  If you have something to say, say it to me.  I go by Faultline.''



\sectionbreak



Faultline pressed her back to the `wall'.  Not that it was really a `wall'.  Labyrinth's power was slowly working on the metal, gradually twisting it into gnarled textures and branches. Shamrock was beside her, clad in a costume of skintight black leather with a green clover on the chest, her red hair spilling over her shoulders, a combat shotgun directed at the ground.  Gregor and Spitfire were on the other side of the door, holding similar positions.



Newter sat with Labyrinth on the bed, his tail circled around the girl's waist, keeping her from wandering.  The bed was barely recognizable, nearly consumed by waist-high strands of hardwood-textured grass.



A cool summer breeze blew in through the opening that had once been the window, scattering dandelion seeds and leaves throughout the room's interior.



``I don't know what she told you,'' the Doctor called out.  ``I always treated her professionally, to the best of my ability.''



``We're not here for revenge on her behalf, Doctor,'' Faultline responded.  ``We're looking for information.''



``I'm not working with the Asylum anymore.  It's been over a year.''



``I know,'' she replied.



``Protocols have changed.  I can't get you past security or anything like that.''



``The Asylum doesn't really interest me,'' Faultline said.  ``Not why we're here.''



``Then why?''



``Because we've been trying to track down people who can give us answers, and you stood out.  Spending a little too much money.''



``I'm a good doctor, that's all!''



``Doesn't account for it.  Comparing you to your coworkers at the asylum back then, you were spending too much money.  Just enough that I think someone was bankrolling you.''



``Your sources are wrong!''



``Don't think so.  I \emph{think} someone was paying you to keep tabs on certain individuals within the asylum.  Was it Cauldron?''



She shut her eyes, listened.  She couldn't make out any telltale gasps or movement.



``I don't know what you're talking about!''



``The other possibility is that you were working for a foreign government.  A spy.  Or, to be more specific, you were working as a spy for \emph{several} foreign agencies.''



``Look at my neighbors!  We do the same kind of work, we live at the same level!''



``Your neighbors are in debt, or they're riding on the capital from smart investments.  You aren't.  Just the opposite.  Your investments are nil, yet you somehow have enough money sitting in the bank that you can coast into retirement.''



``No,'' the Doctor said.



``The difference between you and the other people on my list is that you were stupid about it.  Showing too much of the money.  If it wasn't me who noticed, it'd be one of the people paying you.''



``Nobody paid me!  Your sources are wrong!  I \emph{am} in debt!  Hundreds of thousands!''



``Let's cut past the lies and bullshit, Doctor Foster.  I'm offering you a deal.  You and I both know that you won't be able to maintain this lifestyle if your employers realize you were discovered.  Depending on who they are, they might even take offense.  Either they terminate their relationship with you or they terminate \emph{you}.''



More of the house around them was blowing away, dandelion seeds in the wind.  The wall surrounding the window was gone, and the roof was well on its way to the same state.



``I don't- you're wrong.  These people you're talking about, they don't exist.  I don't know them.''



``Okay,'' Faultline said.  ``Now, I'd have to double-check whether the person paying for the mission is willing to torture or kill you for the information we want\ldots''



She hesitated, glanced at Gregor.  He shook his head.



``\ldotsAnd he isn't.  Isn't that good news?''



``God.  I'm just- I'm a doctor!  I work with politicians, sometimes with big name parahumans.  The- the president's friends come to me!  But I'm only a doctor!  I'm not a spy!''



``Then you have nothing to worry about,'' Faultline said, ``if we leave and we spread the word that we thought you were involved.  If it's an unfounded rumor, then nothing happens.  Maybe your reputation takes a little hit, but a powerful man like you will bounce back, won't he?''



``Please--''



``But if you're lying, if you \emph{are} involved, the people who paid you to keep your eyes open and your mouth shut will be upset.  I don't think you'll be able to escape them by hopping on a plane to some remote country.''



She let the words hang in the air.



``I\ldots if I told you, I would be in just as bad a situation.  Hypothetically.''



``Hypothetically,'' she said, ``I suppose you'd have to decide whether it was better to trust us and our professional, \emph{circumspect }demeanor and the \emph{possibility} that we'd let the details slip or whether you wanted to suffer the \emph{inevitable} consequences if we started talking.''



There was another pause.  She waited patiently.



``I was supposed to find out just how much the United States knew about what was going on.  Like you said, keeping my eyes open.  Twice, putting a special thumbdrive into one of the main computers.  That was for the United Kingdom.  I sent regular reports to another group.  I think they were the C.U.  I didn't do anything specific for them.  Just describing new inmates, recent hirings and firings, changes in policy.''



\emph{The C.U.l  China}.  It was good to be \emph{right}.  ``Did you download anything onto the drives, or--''



``I don't know.  I don't think so.  I was supposed to plug them in, then wait.  After, I took them out and destroyed them.''



``Very possible it was putting a backdoor into place, giving your employer remote access,'' Faultline said.



``Why does this matter?''



``That's our business, not yours.  Did they ever show particular attention to an individual?''



``Some attention for the more powerful ones.  Nothing ever came of it.  I gave them more details, they paid me, that was it.  The patients stayed in the asylum's custody.''



``If you had to, how would you get in touch with them?''



``Email.  Sometimes phone.  They changed handlers.  Been a while.''



``When did they last contact you?''



``Two years ago?  About?''



``Why?''



``Wisconsin.  The Simurgh attack.  There was an open call for civilian volunteers.  My contact from the U.K. left me a message.  Asked me to volunteer my medical expertise, see who was filtering out.''



``Did he have a handle?''



``Christof.''



Her heart leaped.  ``Spell it.''



``C-H-R-I-S-T-O-F.''



A rare smile spread across Faultline's face.  Finally, after weeks of looking, they'd found a connection between two clues.  Christof was a familiar name.  She glanced at the others, and Newter gave her a little `fist pump' gesture, smiling.



``How much did he pay you?''



``He didn't.  I refused the deal.''



\emph{Every clue points to a greater picture, how they operate and where the priorities are.}  In a situation where every piece of information was valuable and every avenue of collecting that information crucial, there was a lot to be said for identifying where the major players \emph{weren't} looking for clues.  It suggested they already knew, they already had agents in play.



If they'd let him go so easily, there might have been others.  But it suggested they were interested in what had happened in Madison.



Which meant her crew had reason to be interested.



``Keep talking,'' she said.  ``Let's talk about some of the other jobs.''



\sectionbreak



``Hate the heat,'' Faultline said.  ``I never thought I'd \emph{miss} Brockton Bay, but the weather was usually nice.  Damn sun's not even up and I'm sweltering.''



``It might be easier to bear if you wore something more\ldots summery,'' Newter commented, eyeing her short-sleeved dress shirt and the black slacks that were tucked into cowboy boots.  She glared at him, and he smirked in response.



She'd have to put him in check or he'd be intolerable for the rest of the day.  ``Maybe I need to get the bullwhip?  Or did you forget the drills?''



Newter groaned aloud.  ``You're on that again.''



``On the wall.  Go.''



Newter leaped across the hotel room and stuck to the wall, one hand planted above his head so he could stay more or less upright, his tail curling around his lower foot.  ``Pain in the ass.  You know I'll have to scrub the hotel walls after to get rid of the footprints before we go.''



``Deal,'' Faultline said.  ``The practice could make the difference between you dodging a bullet and you moving too slow to avoid it.''



Spitfire and Elle stepped out of the bathroom, Spitfire with a towel in hands, drying Elle's hair.



``How are we doing?'' Faulltine asked.



Elle didn't respond.  She chewed slightly on her lip, and her eyes looked right through Faulltine as she glanced around the room.



``I think we're about a three,'' Spitfire said.  ``She brushed her teeth after I put the brush in her hands.  Why don't you sit down on the couch, Elle, and I'll brush your hair?''



``I'll do that,'' Faultline said.  ``Get me a brush and then go finish getting ready.''



``Yes, ma'am,'' Spitfire said.  She glanced at Newter, and Faultline suspected she saw an eye roll there.  Spitfire led Elle by hand in the direction of the couch, let go as Elle got close enough to Faultline.  Faultline led the girl to the couch, then sat on the back of the couch with her feet planted to either side of the girl.



She caught the brush that Spitfire threw across the room and set to brushing Elle's white-blond hair.  ``This is badly tangled.  Were you sleeping in a tree again?''



Elle nodded slightly.



``I'll try to be gentle.  Let me know if I'm tugging too hard.''



Elle nodded again.



Faultline caught a whiff of hot sand, salt, and humid air.



``Don't make water, okay, Elle?''  Faultline said.  ``It's not that we're paying the deposit for the room, but it's a matter of principle.  We're professionals.  We don't leave messes.''



The ocean smell faded away by the time Faultline had stroked the brush five more times.



``Thank you,'' Faultline said.



The `Labyrinth' power would typically clean itself up.  When they'd left Dr. Foster's estate, much of it had been turned to leaves, grass and flowers with electric blue petals.  As the effect faded, the building would be restored.



What Elle's power \emph{didn't} clean up was the aftermath the changes themselves wrought.  If a stone pillar toppled onto a car, the pillar might disappear, but the car would remain crushed.  A fire quenched by water would remain out, even as the moisture faded.



Gregor and Shamrock entered from the hotel room's front door, holding hands.  Both were in their combat gear, with some adjustments made to adjust for the heat.  Shamrock wore black yoga pants and a green sleeveless t-shirt with her clover-leaf symbol on the front in black, her mask dangling from her right front pocket, her shotgun dangling from her free hand.



Gregor wore a fishnet shirt over bare skin, thick canvas pants and a snailshell-spiral mask strapped to his face, with holes worked into the gaps for his eyes.  The dark vague shadows of his organs were visible through the flesh of his broad stomach.



``I'm sorry the rest of us aren't ready to go.  Slow start,'' Faultline confessed.



``It happens,'' Gregor said, in his accented voice.  ``And I know it is almost always Spitfire, Newter or Elle at fault.  Not to say I would fault Elle.  But you should not apologize for any of them.  Only yourself.''



``Frankly, bro,'' Newter said, ``I'm surprised you're even capable of moving.  It's not like you slept a wink, know what I mean?''



Gregor lobbed a glob of goo at Newter, who leaped to the ceiling, cackling.  The slime bubbled away to nothingness.



``I took the role of leader,'' Faultline said. ``It's my job to kick people's asses and get them moving when we have a job coming up.''



``And I'm the client,'' Gregor said.  He'd taken a seat in an armchair, and Shamrock sat in his lap.  Almost as an afterthought, he folded his arms around the young woman.  ``I could ask that you and the team are more casual with this job.  Our destination is going to be there whether we leave before dawn or at sunset.''



Faultline shook her head.  ``I'd rather treat this as I would any job.  If nothing else, keeping everyone on the straight and narrow means they won't get sloppy on our next serious job.''



``Very well,'' Gregor said.  ``Then I'd like to leave within thirty minutes.''



``We'll make it ten,'' Faultline said.  ``Pack everything up.  Spitfire can help Elle get her stuff on.  Elle makes us an exit from the balcony so we aren't walking through the hotel in costume.''



She stood from the back of the couch, and nearly collided with a statue that had emerged from the wall above and around her.  A woman, back arched, hands outstretched to either side of Faultline.



She led Elle to the bedroom, where Spitfire was pulling the last of her fire-retardant gear on.  Her own gear was in a separate suitcase.



Faultline was a believer in doing things right.  Image came secondary to \emph{effect, }and doing the job right was better for image than having the best costume.  Her own costume blended several functions.  A bulletproof vest, lightweight, with a stylized exterior, formed the most expensive single component of the outfit.  She tied her hair back into a crude bun, then gingerly drew the `ponytail' from the side of the suitcase.  Unfolding the surrounding cover, Faultline slowly and carefully used her fingers to comb the fake hair onto a semblance of order.  The bristly hair extension masked a thin, flexible rod in the core, with painted spikes protruding at various angles.  It was all too common for an enemy to reach for the ponytail in an attempt to get her.  Their hands would be impaled on the waiting spikes, if they weren't invulnerable, and the hair extension would come free, giving her a chance to escape.



Belts with various tools and weapons were strapped to her upper arms, forearms and thighs, held in place with suspenders.  Knives, lockpicks, various pre-prepared hypodermic needles, climbing tools, sticks of chalk, a mirror, a magnifying glass, iron wire and more were on hand if she needed them.  She ran her finger over the belts to ensure that each pocket was full.



She checked her semiautomatic, then slid it into the holster at her left hip.  A flare gun went into the holster at the right.  Flowing sleeves that would mask the belts and their contents were buckled on next, followed by a dress with a side pocket that would let her access the gun in a pinch.  The buckles meant that anyone pulling on the fabric would pull it free rather than get hold of her.



It was amusing, just how much of a contrast Labyrinth's costume was.   The robe was easy enough to wear that she could put it on over her clothes.  It was green with a `maze' drawn on the fabric.  There were no safety measures, only minimal supplies and gear.



Faultline donned her mask, more a welder's mask with a stylized crack to see through than anything else, then led the other two girls back into the main area of their hotel room.



Newter had changed, but he didn't need much.  He had handwraps and footwraps that left his fingers and toes free, basketball shorts and a messenger bag slung over one shoulder.  He was the first one to exit the apartment, disappearing out the window, then poked his head back in long enough to give a thumbs up.



Elle opened the window into a proper exit, complete with a staircase leading to the road behind the hotel.  Faultline paused to look at the looming stone wall, only a few blocks away.  Three hundred feet tall, it was all smooth stone.  Parahuman made, no doubt.  The barrier encircled the area the Simurgh had attacked, containing everything within.



Every house and building within three hundred feet of the wall itself had been bulldozed.  She couldn't help but feel conspicuous as they crossed the open area.  It was dark, there weren't any spotlights, but she couldn't help but be paranoid.



``Cell phones are dead,'' Shamrock commented.



Faultline nodded grimly.  Of course there wouldn't be any transmissions into or out of this area.  No messages of any sort would be permitted.  Not even water entered or left the quarantine area, let alone communications or goods.  Anyone still inside was left to fend for themselves with whatever resources they could gather.



She'd checked and double checked the measures authorities were taking, ensuring that the area wasn't being watched for intruders.  There weren't any people on the wall, and the only surveillance was busy keeping an eye out for anyone who might be trying to make it over the \emph{top} of the wall.



Going \emph{through} the wall?  Anyone digging through would be caught by the daily drone sweeps, and anyone trying something faster would make too much noise.



Besides, they certainly didn't expect anyone to be trying to get \emph{in}.



Faultline touched the wall.  She felt her power magnifying around her fingertip on contact.  She just had to will it, and her power would dance around the contact point, leaving a hole a third of an inch across.  If she really pushed for it, it would extend several feet inside the object.



Her power worked better with multiple points of contact.  She touched with her other fingertip, and felt the power soar between the two, running through the surface like a current.



She let it surge outward, and a fissure appeared.



She tapped one toe against the wall, and power surged from either fingertip to the point of her toe, drawing a triangle.  Moving closer to the wall until she was almost hugging it, she moved her other toe against the surface.  Four points of contact, six lines.



Then she \emph{pushed}, literally and in the sense of using her power.  The power surged into the object, the lines widening and she swiftly backed away as the resulting debris settled.



Once the dust had more or less cleared, she could make out a tunnel, roughly door shaped.  Her power had destroyed enough of the material that there was barely any debris on the ground.



``Labyrinth,'' Faultline said, ``Shore it up?  Make a nice hallway?  Taller and wider than this, please.''



Labyrinth nodded.  It took only twenty or thirty seconds before there was a noticeable effect.  By the time they were halfway down the tunnel, there were alcoves with statues in them and torches burning in sconces.



Walking through the tunnel was claustrophobic.  Faultline could handle that, but she could see Shamrock clinging to Gregor.  It made his progress through the narrow tunnel that much slower.



\emph{How fragile civilization is}, Faultline mused, as she emerged on the other side.  Newter clambered up the side of the nearest building for a vantage point.



Some of it was the Simurgh's doing, no doubt, but the thing that made her catch her breath was the degree to which things had degraded.  Windows were broken, plants crawled over the surroundings, a building had collapsed a little further down the street.  Stone was cracked, windows shattered, metal rusted.  The buildings, the cars that still sat in the middle of the street, they looked as though they had been left abandoned for a decade, though it was closer to a year and a half in reality.



It didn't take much.  Animals found their way inside, fires started and spread, and weather damaged the structures.  Once the spaces were partially breached, the wind, sun, rain and temperature were free to wear on the interiors, and everything accelerated.



That damage, in turn, paved the way for other things to take root.  Mold could get into materials and surfaces.  Plants could take root, winding roots into cracks, widening them.  Ice did much the same in the winter months.



Still, it was so much, so fast.



She couldn't help but think about what Coil had said about the world ending in two years.  However it happened, \emph{if} it happened, how long would it be before nature had destroyed every trace of humanity, after mankind was gone?



``Pretty,'' Labyrinth said, as she emerged from the tunnel.  Her head craned as she looked around.



Faultline and Spitfire gave the girl a look of surprise.  It wasn't like her to talk on a bad day.



``You think so?'' Faultline asked.



Labyrinth didn't venture a response.



``Guess you like different architecture, huh?''



Still no response.  Faultline rubbed the girl's hooded head, as she might with a dog.



Gregor and Shamrock were the last ones to exit the tunnel.



``All good?'' Faultline asked.



``A little much,'' Shamrock said.  ``Knowing how tall the wall is, how much pressure's bearing down over our heads\ldots I'm a little claustrophobic at the best of times, and that's worse than the best times.''



``We have some time before we need to pass through again,'' Faultline said, ``Maybe Labyrinth can make it wider, shore it up more so you're more comfortable, for the future.''



Shamrock nodded.  ``I hope so.  Thank you.''



``We're looking for any signs of life,'' Faultline said.  ``Avoid confrontation if you don't have backup.  We patrol this area in a pinwheel formation.  We have four people patrolling, each in a different cardinal direction.  Head three blocks out, turn clockwise, travel two more blocks, then zig-zag your way back to the center.  One person always waits with Labyrinth in the middle, so we have a fortified spot to fall back to.  We take turns staying with her, so nobody walks too long.''



There were nods from each of her subordinates.



``Flare if there's any trouble or any find.  Everyone has their guns?''



Everyone did.



``Gregor and Shamrock babysit during the first patrol, don't need anyone to backtrack, obviously.  Move out.''



It took only a second for Newter, Spitfire and Faultline to choose their individual directions.  Gregor and Shamrock stayed behind.



\emph{Better to give Shamrock a chance to calm down}, Faultline thought.  Her boot heels made noise as she walked.



Doctor Foster had been asked to keep an eye on those being released from the city's quarantine.  Each individual got a tattoo of a bird on one hand or on one arm, marking them as someone affected by the Simurgh.



It had been a short-lived policy, covering only two of the Simurgh's visits to America in the span of four years.  Shortly after the second event, the idea was abandoned.  The idea, that people could take extra caution around anyone with a tattoo of a white bird, only generated prejudice.  The affected individuals couldn't find work, they were beaten and they had their lives threatened.



The outcry had meant it was hard to spread the word about what the tattoos were intended for, and the problem was further exacerbated when some people had started getting the tattoos as a matter of protest.  In some poll a year back, something like six out of ten people had been unable to say why the tattoos existed.



But it wasn't likely that the tattoos were why the Doctor had been asked to oversee this situation.



No.  The person who had assigned the Doctor the job, Christof, most definitely \emph{wasn't} working for the United Kingdom.  Christof was, according to data they'd picked up on a job a week ago, supposedly working for \emph{Cauldron}.



Which meant Cauldron wanted someone expendable that could keep an eye on things.



Faultline noted a message scrawled onto a wall: `three thorn babys seen here may twenty. killed two one lived'.



Just below that line, there was another message, drawn in pink chalk that had streaked where moisture had run across it: `thanks'.



Faultline walked on.  Where doors were obviously open or unlocked, barriers hacked down, she peeked inside.  There weren't any signs of people having resided anywhere nearby.



Her patrol carried her back to Labyrinth, Gregor and Shamrock, and the statue-topped gazebo that Labyrinth had put together in the meantime.  Newter had returned and was looking out from a nearby perch.



``No luck?'' Shamrock asked.



``Signs of life, not too long ago, but no people.''



Gregor put down the backpack he carried and handed Faultline a water bottle.



Newter scaled his way down the side of the building nearly as fast as if he'd fallen, arriving a few seconds before Spitfire returned.



``Anything?''  Faultline asked.



``Ominous graffiti, not much else.''



``Those\ldots spine babies, was it?''



``No,'' Spitfire said.  ``I couldn't read it all.  Very broken English.  But it said something about a Devourer.''



``Let's move.  We move up six blocks, then do another patrol,'' Faultline said.  She thought about the Devourer, and the fact that the number one priority of the people in this place seemed to be warning about the local threats.  ``And, until we're out of here, we walk with our weapons at the ready, flare guns in hand.''



They moved up to the next location, moving deeper into the city.  Faultline was pleased that she didn't have to order her team to hold formation.  They were practiced enough that they did it naturally.  Newter scouted out front, Gregor took the rear.  Shamrock took the right flank, shotgun at the ready, and Spitfire took the left.  Faultline moved in the center with Labyrinth.



She called the group to a stop when they had traveled far enough.  When they paused to look at her, she gestured for them to move out, staying with Labyrinth.



``Sorry to drag you around like this,'' she said.  ``Do you feel thirsty?''



Labyrinth shook her head.



``I know new places don't help you feel more lucid,'' Faultline said.  ``And it's more than just today.  We've been going from city to city, doing a series of jobs to try to dig up more info.  I wanted to say thank you.''



Labyrinth only stared around her, looking at the buildings.



``Maybe you want to stay here?'' Faultline asked.



Labyrinth shook her head once more.



``Well, I'm glad.''



A flare detonated overhead.  Faultline whipped her head around.  \emph{Newter}.



She bolted in the direction he'd gone, holding Labyrinth's hand, pulling the girl after her.



When she saw Newter, she stopped, let herself breathe.



Civilians.  Five of them.  They were wielding improvised weapons.  A makeshift bow and arrow, spears.  Nothing that posed a serious threat to Newter.



``These are my friends,'' Newter said.  He was holding his hands and tail up in the air.  ``More will be coming shortly.  We're not here to hurt anyone.''



``Why \emph{are} you here?  You're insane, coming to a place like this.  You know what the Simurgh does.''



``We do,'' Faultline said.  ``But we have a friend, she's got a bit of precognitive talent.  Enough that it should clear us of any schemes the Simurgh is pulling.''



Eyes went wide.



``We're looking for answers,'' Faultline said.  ``Information, either about or \emph{from} the monsters who came through that portal the Simurgh made.  Give us something to work with, we'll show you how to leave.''



``Assuming we want to,'' one man said.



\emph{Why wouldn't you?}  Faultline wondered.  She chose to be diplomatic and keep her mouth shut.  ``Assuming you want to.  I'm sure we could come to another deal.''



``Why do you want to talk to the monsters?'' the woman with the bow asked.  She had improvised urban camouflage paint over her face.



Faultline gestured in Newter's direction, was aware of Gregor and Shamrock arriving.  She turned her head to see Spitfire coming around the corner.  She gestured at her teammates, ``These guys are my friends, and they're my employees.  We want answers about why this happened to them.  Once we have those answers, we decide where we go from there.  If nothing else, it's valuable info.''



``You're on \emph{their} side?'' a man with a spear asked.



``Yes,'' Faultline said.  ``But I could be on yours too.''



The woman with the bow stepped away from her comrades.  Her weapon pointed in their general direction.  ``You have a way out?''



``Yes.''



``And you just let us go?  There's no catch?''



``No catch.''



``I\ldots how do I know I can trust you?''



``You are one of us,'' Gregor said.



The woman froze.



``Maddie?'' a man asked.



``How did you know?'' Maddie asked.



``I know this feeling, of being lost.  Of being very alone and not knowing who can be trusted,'' Gregor said.



``How can I believe you?''



``Because we've been where you've been.  These two don't remember, they had their memories taken,'' Shamrock said, ``But I didn't.  I remember what it was like in there.  And I get why you're afraid.''



``You were in there?''  Maddie asked, her eyes going wide.



Shamrock nodded.  ``One moment, I was going to bed in my temple-school.  In another, I was in a cell.  A cot, a metal sink, a metal toilet.  Three concrete walls, a concrete floor and ceiling, and a window of thick plexiglass with a drawer.  You might know the kind of cell I'm describing.



``They drugged me, then they waited until I started showing signs that something happened to me.  It took them a while to figure out, because my power was subtle.  When they had an idea of what I could do, they gave me a coin.  I had to flip it when the doctor came.  If it came up heads, I got to eat, I got fresh clothes, a shower.  If it didn't, I got nothing.  I realized I was supposed to control it.  \emph{Decide} the result of the toss.  When I got good at it, they gave me two coins, and both had to come up heads.''



``How long were you there?'' Maddie asked.



``I don't know.  But by the time I saw the chance to escape, I had to roll twelve dice and each one had to come up with a six.  And if it didn't, if I got more than a few wrong, they found ways to punish me.''



Gregor put his hands on Shamrock's shoulders.



``They made me use my power.  I\ldots I think I was one of the people they used to punish the ones who failed their tests,'' Maddie said.



``Christ,'' one of the men said.  ``And the freak has been with us for a week?''



Maddie turned to glare at him.



``If it means anything,'' Shamrock said, ``I forgive you.  You didn't decide to punish anyone.  We did what they made us do.''



Maddie flinched as though she'd been struck.



``Come with us,'' Faultline said.  ``You don't have to \emph{stay} with us, but we want to hear what you have to say.''



``I'm a predator,'' Maddie said.  ``Not because I want to be.  You don't want me to be near you.''



``You were around \emph{them} for at least a little while,'' Faultline said.  ``You can be around us for a few hours.''



Maddie glanced around, then nodded.  ``When\ldots when they tested you, did they give you a name?''



``They gave me a number at first,'' Shamrock said.  ``I couldn't use my real name or they'd punish me.  When I passed a year of testing, they let me pick a codename.  I picked Shamrock.''



``I wouldn't pick,'' Maddie said.  ``So they gave me one.  Matryoshka.  I\ldots I don't deserve my old name.  So call me by that one.''



``Layered doll,'' Faultline said.  Matryoshka nodded.  ``Let's go.  We'll leave the quarantine area, get you some proper food while we talk.  If need be, we'll come back and see if we can find more people.  If you wanted to guide us for a return trip, maybe direct us to others, I could pay you.  Get you on your feet in the outside world.''



Matroyshka smiled a little at that.



\sectionbreak



It took a little while to verify that everything was in order at the hotel.  Nobody had noticed their exit and there weren't any law enforcement officers stationed nearby.



They entered the hotel room much the way they'd left, with a makeshift ladder leading to the balcony, and quickly settled in.  Matryoshka gorged herself on the groceries Faultline had bought shortly after they'd arrived.  She stared wide-eyed at the television.  It was the first time she'd ever seen one.  It led to her excitedly describing her world between mouthfuls of food.



Faultline visited the bathroom, then stopped as a square of white caught her eye.



A note?



She opened the door to verify it wasn't attached to anything, then pulled it into the room with the toe of her boot.  Closing the door, she unfolded it with her toe to verify that it didn't have any powder inside.



Only a message: `Front desk.  Message from Brockton Bay.  ASAP.'



Brockton Bay?  Faultline frowned.  That would be Coil.  He was the only one with the resources to get ahold of her group.



She was loath to leave Madison while they were having some success pulling in more information on Cauldron's operations, but\ldots Coil \emph{did} pay well.



Well enough to warrant a phone call.



She headed down to the lobby in civilian clothes, with Shamrock as backup.



Oddly enough, there was a wait at the front desk.  A young woman, dark-haired, wearing a suit and fedora, with luggage on wheels.



\emph{Arriving} a\emph{t four in the morning?}



The woman smiled and tipped her hat at Faultline as she headed to the elevator.  Faultline watched her with a touch of suspicion.  She didn't relax when the elevator doors closed.  She watched the floor number for the elevator tick upward until it stopped at `four'.  Two floors above the rooms her team was in.



``What is it?''  Shamrock asked.



``Gut feeling.''



``About the woman?''



``Just\ldots felt wrong.  Do you mind going upstairs?  Check on the others?  Maybe tell them to be on guard, and get all the nonessentials packed up.  Might be paranoid, but I'm thinking we should change hotels.  Good enough chance we were seen, worth doing anyways.''



Shamrock nodded and headed for the staircase.



``You had a message for me?''  Faultline asked the woman at the front desk.  ``Room 202.''



``Yes.  A phone number.''



Faultline nodded.  She took the piece of paper with the number, then stepped outside to call it on her cell.



The person on the other end of the phone picked up on the first ring.



``Yes?'' Faultline spoke into the phone



``This is Tattletale,'' the voice came through.



``Fuck me.'' Faultline groaned.  ``How the hell did you find us?''



``Long story.''



``What do you want?  We're not available for any jobs.''



``Don't want to hire you for a job.  In fact, bringing your guys into the current situation would be a fucking bad idea.  Pretty much all of you are\ldots well, let's say it'd do more harm than good.''



``You're wasting my time, Tattletale.''



``It's been a long night.  Cut me some slack.  I want to borrow Labyrinth.  I don't care how many of the rest of you come.  Non-combat situation, use her powers.''



Faultline paused.  ``Why do you want her?''



``Because I have a group of people here with very little to lose and nothing left to hope for, and I need them on our side.  I think Labyrinth can give them what they want.''



``Labyrinth's powerful, but I can't imagine any situation where she'd be able to give anyone what they wanted.  Her power's temporary.  The kind of stuff you could do with her power\ldots there's easier ways.  Other people you could go to.''



``I think,'' Tattletale said, and she managed to sound condescending, ``That I understand her power better than you do.''



Faultline considered hanging up.



She sighed, then raised the phone back to her ear.  ``You wouldn't be baiting me if you didn't think you could get away with it.  Cut to the chase.  What are you offering?''



``Three point four million.''



Faultline blinked.  Her surprise at the sum was tempered only by irritation that Tattletale had managed to get her hands on that kind of money.  ``Double it.''



``Done,'' Tattletale said.



\emph{A little too fast.  I'd think she was lying, but that's not why she was so fast.  She expected me to make a counteroffer.  Probably decided the first amount with that in mind.}



Faultline grit her teeth in annoyance.  ``I want it in advance.''



``Sure,'' Tattletale said, sounding far too pleased with herself.  ``And done.''



\emph{A little too fast, again.  She had that set up, damn her.  }``You have my account information?''



``Coil did.  Don't worry about it.''



Faultline hung up in irritation.  She considered taking the money and refusing the job, but she -and Tattletale- knew her reputation as a mercenary was too important.



\emph{Should have refused.}



She made a beeline for her hotel room.  She'd need to check the account information, then move funds to an account Tattletale \emph{didn't} know about.



A glance at the display above the elevator showed that it hadn't moved.  Faster to take the stairs to the next floor than to wait.



Her heart skipped a beat when she heard the screaming.  Faultline flew up the stairs to the door, pushed her way into the second floor, and raced down the hallway to the hotel rooms.



There was blood on the door as she pushed it open.



How to even take this sort of thing in?  How to describe it?



Her team had been destroyed.



Gregor was in the kitchen, on his back.  His chest heaved, and he'd covered much of his upper body in a foaming slime.  What she could make of his face was contorted in pain, scalded a tomato red that was already blistering.



One of Newter's arms, one of his legs and his tail had each been broken in multiple places.  The remains of the coffee table, the flatscreen television and one door of the television stand lay around him, where he'd sprawled into them.



Matryoshka had unfolded into a mess of ribbons, but knives from the belt Faultline had removed to go down to the lobby had her pinned to the wall in six different places.



Labyrinth was the one screaming, steady, almost rhythmically, with little emotion to it.  From the lack of affect, Faultline might have assumed she was in shock, but it was simply the fugue from her power.  A small mercy – two thin cuts marked her face, and one hand was impaled to the armrest of the couch by another of the small knives.



Shamrock was busy giving Spitfire a tracheotomy.  A fedora filled with slime was plastered to the younger girl's face, and she was struggling weakly.  Shamrock's own face was covered in blood from nose to chin, and her efforts to administer the tracheotomy were limited as the fingers of one hand were bent at awkward angles.



``The woman in the suit,'' Faultline said, dropping to Spitfire's side.  She noted the slime.  \emph{Gregor's}.  And Gregor had been burned with Spitfire's breath?  ``Power thief?''



Shamrock let Faultline take over, positioning the clear plastic tube that was sticking into the hole in Spitfire's throat.  She had to spit blood out of her mouth before speaking, ``No.  I don't know.  She came in here and took us apart in twenty seconds.  We didn't touch her.''



Spitfire coughed, then started breathing at a more normal rate.  She gave Faultline two pats on the wrist, calmer.  A signal of thanks?



``Super speed?  Super strength?''  Faultline asked.



``No.  Don't think,'' Shamrock spat blood onto the floor.  She tried to stand and failed, put one hand to her leg.  ``Nothing I could see.''



``A thinker power.  Precognition?  No, that wouldn't work with your power.  Fuck!''  Faultline scrambled to her feet, hurried to Labyrinth's side. ``Hey, Elle, calm down.  It's okay, it's over.  Stop screaming.''



Labyrinth shut her mouth, whimpered.  The cuts to the face were thin.  They'd heal with little to no scarring.  The hand-



Faultline stopped.  There was a piece of paper beneath the hand.



She helped Labyrinth raise her hand where it was impaled, leaving the knife in place.



The bloodstained piece of paper had a message on the underside.



Final warning.
-c





