





Brian was waiting for me as I passed through the door and into Coil's underground base.  He held a paper out to me.



Sirs and Madams,



The terms of engagement are as follows:
1.  Three days to each member of the Slaughterhouse Nine so we can conduct our tests.  Tests will be performed one after the other, with eight rounds in total.
2.  A successful test or the removal of a candidate who has failed a test will earn the tester bonus time.  3-12 hours for a successful test depending on the number of candidates remaining and 24 hours for an execution.
3.  Should a tester suffer a sound defeat at the hands of any individual during their allotted time, they will be penalized one day of allotted time.
4.  Each tester operates independently, with no hands-on assistance from other members of the Slaughterhouse Nine.  Assistance may be bought, bartered or otherwise rendered in a hands-off manner, possibly including medical assistance, information, provided equipment and suggestions.
5.  \underline{Candidates} may receive assistance, hands-on or otherwise, from Brockton Bay residents only.  We are fully aware that Legend and his teammates are in Brockton Bay.  Should they interfere with a tester, all candidates will lose the protection of any rules, all terms offered here will cease and the threat implied in point eight will be carried out.  This only applies to confrontations with the \underline{active} tester.
6.  The Slaughterhouse Nine will handle the punishment of any members of their own team, in the event of failures, the inability of the tester to perform at least a partial round of testing or killing a candidate without notification.
7.  Should the defending parties have two or more candidates remaining when the eighth round of testing concludes, the Slaughterhouse Nine will depart Brockton Bay without incident and refrain from returning for three years at a minimum.
8.  If and when the Slaughterhouse Nine do eliminate five of the six candidates, or if any candidates leave the city, the Slaughterhouse Nine are prepared to penalize the city for their failure.



Mannequin is the first to carry out his round of testing.  He has two days remaining.



We will be in touch.



``Where is everyone?'' I asked, handing the paper back to him.



He pointed down the hall.



``Christ,'' Brian said, shaking his head as he walked, rereading the terms.  He opened the door for me.



Coil was inside, at the end of a long table.  The Undersiders sat at one side of the table, with Circus sitting at the farthest edge, beside Coil.  The Travellers, minus Noelle, sat along the other side.  I took note of the blond teenager who wasn't even wearing part of a costume.  Oliver.  Coil was the opposite, as fully covered as ever.  Everyone else was costumed but they had their masks and helmets off.



I got my first good look at Lisa since I'd left her bleeding in Ballistic's headquarters.  The scar ran from the corner of her mouth to the corner of her jaw, and dark stitches ran down the length of it.  The slang term for this kind of injury was a Glasgow smile or a Chelsea smile, but the term seemed ill-fitting.  Where Lisa often had a grin on her face, the cut pulled the corner of her mouth down into a perpetual lopsided-frown rather than a smile.



Bitch gave me a dark look as I entered, but many of the others were smiling.



``The people in my territory are singing your praises, Skitter,'' Ballistic said.



``My territory too,'' Alec added.



``I didn't do anything that special.  My power did the work.''



``And you kicked Mannequin's ass,'' Trickster said.  He leaned back in his chair, balancing on two of the legs, his feet on the table.  ``You had a busy night.''



``Honestly, I didn't kick his ass.  He got some of my people, he thrashed me, I got a piece of him.''



``No,'' Lisa said, her voice quiet.  She couldn't really move one corner of her mouth when talking, so her words came out slightly slurred.



I saw her work her tongue in her mouth and then take a sip of water, wincing.  Brian had updated me: the cut had probably damaged one or more of her salivary glands, and she'd have dry mouth until it healed.  Maybe forever.  The really scary part was that she might have suffered some nerve damage as well.  How much of that half-frown was because of the direction of the cut and the way the stitches pulled, and how much was because her nerves were damaged enough that her face was drooping?



She caught me looking and gave me a wink.  She took another gulp of water and cleared her throat before speaking again.  ``They took one day from Mannequin because \emph{they }thought he lost.''



``If the enemy thinks they lost,'' Brian said, ``That's a good enough reason to think you've won.''



I privately disagreed, but I didn't say anything.  I pulled up a chair and sat at the corner of the table furthest from Coil, wincing at the pain in my ribs as I bent down.



``So,'' Brian said, ``You intend for something like this to happen when you made your suggestion, Tattletale?''



Lisa shrugged, ``Sorta.  Thought he'd take the bait, didn't know how far.''



``It's not all advantageous,'' I said, thinking aloud.  ``Yes, we're now in a position where we could win, with some planning or luck, and the plan we were hashing out at our last meeting might be easier, now.  \emph{But} we're also facing pretty heavy consequences if we fail\ldots \emph{heavier} consequences.  And there's a lot of places where this could go wrong.  We don't even know who all the candidates are.''



``Me, Bitch, Armsmaster, Noelle, probably Hookwolf and someone in Faultline's crew?''  Alec said.



``No.  Jack said they picked two heroes.  Hookwolf, yes.  But their last pick is a hero, not one of Faultline's,'' Lisa said.



``And we can't say for sure who this person is or what actions they plan to take,'' I said.  ``Too much hinges on everyone else's willingness to cooperate and play by the rules, and the stuff that happened at the last meeting of the city's villains makes me skeptical.''



Brian nodded.  ``It's important that we find this person, make sure they play along, so we don't wind up losing before this game of theirs even starts.''



``There's other problems here,'' I said, ``We can't forget what Dinah said about Jack.  If he leaves town, it could mean disaster.  If we \emph{win}, we could all lose in the long run, because it'd mean he left town and Dinah's prophecy would come true.  Hell, a lot hinges on whether the Protectorate is on the same page as us.  If they arrest him and take him out of town\ldots''



``It could mean the end of the world.''



``Right,'' I said.



``Hookwolf has proposed an all-out attack,'' Coil spoke for the first time since my arrival.  ``He wants to gather the more powerful members of his alliance together into an army and attempt to overwhelm the Nine and kill Jack Slash in the chaos.''



``That won't work.''  Brian shook his head.  ``These guys specialize in dealing with crowds, and they're experienced when it comes to that sort of thing.''



``Hookwolf believes our local capes are collectively strong enough to do what other groups couldn't.''



``Maybe they are, but I wouldn't bet on it.  We should be focused on what \emph{we} can do,'' Brian said.



``You guys are better set up for information gathering and escapes,'' Trickster said.  ``We could take them on, depending on who it is and how small the group is, but I don't know how well we'd do in those circumstances.''



``We should mix up our teams, then,'' Brian said.  ``Just between us, we've got three candidates.  Noelle, Regent and Bitch.  Three targets.''



``Crawler couldn't reach Noelle where we've got her stashed,'' Trickster said, ``I'm not sure what the others could do.''



``What about when Siberian comes after Noelle?'' I asked.  ``Will the same measures stop her?''



``Probably not,'' Trickster replied.



``This would be a lot easier if you'd tell us more about her,'' I pointed out.  ``Unless you think she can hold her own against the Nine, we're going to be helping protect her.''



Trickster frowned.  ``There's not much to say.  She's in containment, and if she doesn't stay where she is, things would get worse, fast.''



``So she's dangerous, and she's not entirely in control of her power?''



He tilted his chair forward until it was flat on the ground and set his elbows on the table, hands clasped in front of his mouth.  He glanced down the table at his teammates.  I wasn't sure, but I thought maybe he glanced briefly at Coil.



With a resigned tone, he told us, ``She's dangerous enough that if Siberian got to her, I think she'd make it out okay.  The rest of us wouldn't.''



The table was silent for a moment.  I could see something in the faces of the Travelers.  Pain?  It wasn't physical, so perhaps it was emotional?  It could be fear, guilt, regret, or any number of other things.



Trickster's words reminded me of what Sundancer had said back when she and I had fought Lung.  Sundancer had held back in using her power because she was frightened about hurting bystanders or killing the people she attacked.  Her power was too hard to use without hurting someone.  Ballistic was the same.  Was Noelle another case of the same thing?  That same too-powerful ability, only on a greater scale?



Brian sighed.  ``We'll deal with Noelle's situation when it comes up.  We have three targets they're going to be coming after, with a fourth if we consider that Mannequin'll be after Skitter.  If we split into two groups, then we can maintain enough offensive power to defend ourselves against the ones like Mannequin, Burnscar, Jack or Shatterbird.''



Sundancer cut in, ``Which makes me wonder\ldots  Sorry if this is a crummy idea, but what if we waited for Jack's turn, and then tried to kill him?''



``No guarantees there,'' Brian answered her.  ``I think we'll have to be proactive in going after him.  Maybe we can use Hookwolf's distraction, maybe he'll get cocky and make a mistake.''



``Doubt it,'' Tattletale said, ``He's lasted \emph{years} doing what he does.''



I couldn't help but nod in agreement.



``Besides, he goes last,'' Tattletale finished.



``To get back to what you were saying, you were proposing dividing the teams?'' Coil spoke.



``Yeah,'' Brian said.  ``Bitch has offensive power of her own.  Skitter does too.  If there's no complaints, we could play this largely geographically.  Maybe me, Imp, Bitch and Skitter?  If you guys can put your differences aside?''



``No problem,'' I said.



``Whatever,'' Bitch answered, noncommital.



It was only when Brian mentioned Imp that I realized Aisha was present.  I'd almost missed her.  I wanted to believe that it was because she was sitting at the end of the table and there were four of my teammates between us, but I couldn't be sure.  It would be \emph{damn} nice if there was some sort of gradual immunity to her power.



``And maybe someone else who isn't raw offense?  Circus?''  Brian suggested.



Coil spoke before Circus could reply.  ``No.  I pulled her off of a task as a precautionary measure, as I had one aspect of my long-term plans derailed last night with Trainwreck's demise at the Nine's hands.  I would rather she did not fall to an unfortunate coincidence of the same nature.''



``What happened?''  Sundancer asked.



``They've eliminated the Merchants,'' Coil said.



I wasn't sure how to feel about that.  The Merchants were scum of the worst sort.  It wasn't just that they polluted everything they touched and did some reprehensible things.  They reveled in it.  They \emph{wanted }to be the lowest of the low.  On the other hand, it was a point for their side.  Seven or eight parahumans we no longer had to fight the Nine with.



``Also, I would prefer her involvement in my operation stay under wraps.  She can defend Noelle and myself for the time being.''



``Then Trickster?  Or Genesis?''  Brian asked.



``I would rather stay close to Noelle,'' Trickster said.  ``If Genesis is willing, that would be fine.''



``And that leaves Ballistic, Sundancer, Trickster, Noelle, Regent and Tattletale for the second group.  We stay together, we keep an eye on our territories to watch for trouble from Hookwolf's contingent, and we keep an eye out for opportunity.  Tattletale?  You're good watching the downtown areas?''



Lisa nodded.



``And Skitter has the sensory abilities to check areas of the Docks where the Undersiders have territory.''



``I'll need to visit each area in turn.  Unless we have some people to pass on messages, and a means of communication.''



``I arranged a delivery,'' Coil said.  ``You'll each be provided with a satellite phone before you leave, with mobile phones to use when the towers are in operation again.  It won't be immediate, but I have shipments of new generators, appliances, laptops and other necessities on the way.  With the information Hookwolf has provided us about Shatterbird's power, I think we could shield the most necessary pieces of equipment with soundproofing in case of a repeat incident.''



``My bugs \emph{did} hear something just before the blast hit,'' I said.  ``Is her power ultrasonic?''



``Something like that.  Tattletale believes that Shatterbird's power causes glass to resonate at a very particular frequency, where it generates that same resonation in other pieces of glass with the aid of her power, perpetuating the effect until it runs out of large pieces of glass to affect.''



``And,'' Lisa said, ``She probably has a reason for hitting the entire city like she does.''  She took another drink of water.  ``Big pieces of glass help transmit the signal, maybe smaller shards help her in another way.  Probably helps or allows more delicate movements.''



``I'm not saying I'm not happy to be getting more concrete information on how they operate.  I just wish it was against the ones we don't have any idea how to stop.  Like Crawler and Siberian,'' I said.



``We use the same strategy we used to fight Aegis,'' Brian said.  ``When fighting an opponent who won't go down, you run, you distract, you occupy them with other things, and you contain them to buy yourself time to do what you have to do.''



He was right.  It just wasn't ideal.  Avoiding or containing them was easier said than done, for one thing, and it was less an answer than a stopgap measure.



``We've addressed the most pertinent crisis, then,'' Coil said.  ``Is there anything else?  Any ideas or requests?''



``I had an idea,'' Aisha said.



``\emph{No},'' Brian said.  ``I know what you're about to say, because we talked this over.  It's a \emph{bad} idea.''



``Let's hear it,'' Trickster spoke up, leaning forward.  Brian scowled, and Aisha smiled wickedly.



``The biggest threat from these guys is that they could strike at any time, from any direction.  So why don't we spy on them?  We find out where they are, and then we keep tabs on their movements.  I can handle one shift, Genesis does the next.  They won't notice me, and Genesis can stay concealed.''



``It's far too risky,'' Brian said.  ``You joined this team so I could \emph{stop} you from getting yourself killed.''



``It \emph{would} be nice to know what they're up to,'' Trickster cut in.



``They won't even know I'm there.''



``You \emph{think} they won't know you're there,'' Brian said.  ``There's a distinction there.  It's important, and it could either lead to a minor advantage-''



``A \emph{huge} advantage,'' Aisha said.



``-Or it could lead to you being turned into a human test subject for whatever fucked up idea Bonesaw had recently,'' Brian finished, ignoring her.



``No!  I got a power, and it's a \emph{useful} power.  Except you don't want me to use it, because you think it's going to stop working all of a sudden, or someone is going to see me-''



``\emph{Dragon} saw you,'' Brian said.  ``And you're only alive because she doesn't kill people.''



Looking at Brian and Aisha, I knew this discussion would get worse before it got better.  I cut in before either of them said something regrettable.  ``Imp.  It's a good idea, but they \emph{do} have a way of sensing you.  Cherish can sense emotions, and if Dragon is any indication, your power primarily works through sight, hearing and touch.  Like Grue's.  She can probably find you and track you down.''



``We don't know that,'' Aisha said.



``It's a pretty good educated guess, I think.  I know you want to be useful, but we can make more use of you if you're with us, going up against someone like Mannequin or Shatterbird, who are far less likely to be able to see you.  Help us defend ourselves.''



``This sucks!''



``Imp,'' Grue said, as he glanced at the others at the table and frowned, ``We're in the company of our employers and our peers.  Let's stay professional and discuss this after.''



``\emph{Professional}?  You asshole, you're the one who's refusing to use my talents because I'm your \emph{sister}.  I've been on the team longer than \emph{Skitter} was when you guys were robbing a bank and fighting the ABB.''



``You're younger, and she's more level-headed-''



``Enough,'' Coil said.  It served to shut them both up.



For a few seconds, anyways.  Aisha scowled.  ``Enough is right.  I'll see you guys later.''



``Hey!''  Brian stood from his seat.



I think I wasn't the only one to look up at him and wonder why.  He looked at us, similarly confused, and then sat down just as quickly as he'd stood.



Lisa looked pensive.  I nudged her and asked, ``You okay?''



``Yeah,'' she replied.  Then she looked at Coil, ``Hey, while you're asking for suggestions, I have an idea?''



``Anything helps.''



``You think you could get your hands on some surveillance hardware?  Skitter's working on some new costumes, and I was thinking we could have something like small cameras mounted on our masks or helmets.''



``I can inquire with my usual suppliers.  Why?''



``Well, we've got one teammate that's sort of hard for the rest of you to keep track of, and I think it might help.  And if nobody objects, I'm kind of wanting to take a less hands-on approach from here on out.  I've batted a pretty low percentage as far as injuries over the last few months of action\ldots Glory Girl, Bakuda, Leviathan, now this incident with Jack.  If I had a means of communication and the gear to give me some eyes on the scene, I think I could be \emph{more} useful.''



Coil looked at Brian.



``I gave you a hard time about your having to take the same risks as the rest of us, back when you first joined, but I think you've done your share.  So long as you're contributing,'' Brian said.



Coil nodded. ``I'll see what we can prepare.''



Lisa smiled a little, using only the one side of her mouth.



\blacksquare



Our canine mounts raced through the streets with impunity.  The glass that covered the roads, the lack of windows, windshields or working dashboards in the few cars that still ran all contributed to the glacial pace of traffic.  There was little for the dogs to watch out for, no moving vehicles and few bystanders.  Every stride the dog took made the bag I was carrying bang against my hip and made every injury I had explode with pain.  I clenched my teeth and endured it.  There weren't many other options.  I could hardly complain to Bitch.



Bitch was well in the lead, and there was a kind of aggression to how she rode.  She pulled ahead, evading cars by only a couple of inches, forcing them to swerve, and she goaded Bentley faster with kicks and shouts.



We hadn't raised the topic of Bitch and her nomination for the Nine.  I think the others hadn't wanted to add tension and the possibility of argument or violence to the already complicated situation.  I know \emph{I} hadn't.  My last real interaction with Bitch was when we'd parted ways after the fight with Dragon.  I'd told her we were even, but there had been some anger and hurt feelings on both sides.  I was the \emph{last} person she wanted to have grilling her.



Bitch made Bentley slow to a walk as she reached my territory.  It still took us a good thirty seconds to catch up.



Using my power, I signalled Sierra and Charlotte.  Grue, Bitch and I climbed down from our dogs and then led them forward.



``Mannequin slipped by you once,'' Grue said.  ``You going to be able to keep an eye out?''



``I had some ideas, but I'm running low on resources,'' I said.  ``Let me see what I can do.''



Genesis began to appear a short distance away, near Bitch.  A blurry, beige and yellow, vaguely human-shaped figure coalesced into being.  The shape then sharpened into features and alter in hue until there was the figure of a teenage girl, vaguely cartoonish.  By the time we reached her, she looked indistinguishable from a regular girl.  She had auburn hair, freckles, and thick glasses.  A small smile touched her face as she stretched her arms and legs.



``Everything good?'' Grue asked her.



``Good enough.  I'm going to keep this shape until Coil's people can deliver my real body.  Then I'll need to recuperate some.''



``Sure.''



Bitch scowled at me.  Bastard, her puppy, stood beside her.  He had received the brunt of her power, and looked roughly as large as an adult great dane.  The features were different from her usual dogs.  The spikes had more symmetry to their arrangement, and the muscles looked less like tangles.  It tugged briefly on the chain that led from her hand to its collar, and she pulled back sharply.  It didn't pull again, though it was easily powerful enough to knock her over.



My people met us as we entered the neighborhoods where my lair and the barracks we'd set up were.  Sierra and Charlotte were in the lead, the three ex-ABB members behind them.  The O'Daly clan stood at more of a distance, all either members of the family, friends or romantic partners.  Other, smaller families filled in the gaps.  My `gang' numbered nearly fifty people in total.



``Holy crap,'' Genesis said.



``It's why we wanted to set up base here,''  Grue said.  ``Skitter's the most established of us.''



``I've been focusing on structural repairs and building when I'm not helping my teammates,'' Genesis said.  ``I don't have many threats to get rid of, and it was the best way for me to be productive.  And meanwhile you're further than I expected to get in half a year.''



I couldn't bring myself to feel proud.  ``I guess I'm motivated.''



Genesis whistled, looking around.  There were some looks of confusion as she strode forward into the crowd.  I suppose it was unusual for a teenage girl to be in the company of three known supervillains and a mass of monstrous dogs.



``Sierra,'' I said.  ``Status?''



``We're nearly done with the second building.  There isn't a lot of elbow room, so we've been cleaning up the road.''



``Good.  No trouble?''



``Not that I know of.''



I pulled the bag from over my shoulder and handed it to her.  ``Distribute these to the people in charge of the various groups.  Work it out so you can pass on messages quickly, and get any necessary information to me asap.''



``Okay.''  She grunted as she took the bag.



``Genesis,'' I spoke.  ``You said you were doing some rebuilding?''



She slapped her stomach, ``Made some mortar, just a matter of sticking stuff back where it's supposed to be, if it's obvious enough.''



``Want to see what you can do, before your body gets here?''



She nodded and headed off.  My minions rapidly backed away from her as she began dissolving.



``Charlotte?''



``Yes?''



``How set up is the building you guys were working on?''



``Mess is cleaned out, but we haven't moved much in.''



``That should be fine.''



``We ready?'' Grue asked.



I turned to face him and Bitch.  ``Just about.  Bitch, there's a space set aside that we can use for your dogs.  We'll patrol through the various territories in an hour or so, stop by your territory and pick up some supplies for them, and you can bring your dogs here.''  I had to resist adding an `if that's okay'.  Firmness would work best with her, even if it did carry the risk of provoking her.



``Fine.''



``Good,'' Grue said.  ``Let's go rest and eat.  We can wait for Genesis and the other gear Coil's dropping off.''



I had enough bugs nearby to start setting up my early warning system.  With the assistance of a horde of flying insects, I began guiding spiders through various points of my territory.  They drew out lines of silk across alleyways and doors, windows and rooftops.  I couldn't spare the spiders, so I placed ants on each line.  They would feel it if there was a vibration, not as well as the spiders, but well enough.



Ten thousand tripwires for Mannequin to navigate past.



My expectation was for the lines to maybe give me an early warning of Mannequin's approach, sometime in the coming hours, maybe in the dead of night.



I didn't expect to find him in the span of a minute.  A figure on a nearby rooftop was striding through the webs and avoiding the bugs.



I stopped.  ``Mannequin.''



Everyone else froze.  Even the dogs seemed to mime their master's stillness.



But he was already leaving, moving with surprising swiftness as he pushed through another few lines of webbing at the edge of the roof furthest from us.  A second later he was on the ground, moving through an alleyway.



``We could go after him,'' Grue asked.



``We couldn't catch him, I don't think,'' I said, ``And he may be trying to bait us into a trap.  Or maybe he wants to loop around while we give chase and kill my people.  Shit, I didn't think he'd come so quickly.''



``We weren't exactly inconspicuous.''



I frowned.



Mannequin was on guard for a trap, enough that he'd probably noticed the tripwire and decided to retreat.  Mannequin and I had an estimation of one another, now.  Neither of us wanted a direct confrontation.  Both of us would be wary of traps or trickery.  He was a tinker, he would have prepared something to ward against the tactic I had employed last time.  Topping it off, amassing people to please Coil had the unfortunate side effect of making me more vulnerable to Mannequin's attacks.  He could hurt me without even getting close to me, the second I let my guard down and gave him an avenue for attack.



The only ambiguous advantage we had over him was that he was working with a time limit.  He needed to test Bitch and get revenge on me, in addition to dealing with all of the other candidates, and he had less than forty-eight hours to do it.



I wasn't so sure that was a good thing.  It was beginning to dawn on me what we were in for.  Forty eight hours of being on the edge of our seats, unable to sleep deeply, constantly watching for attack from Mannequin or from Hookwolf's contingent.



When we were done, we faced seventy-two hours of the same thing.  We'd be that much more tired, that much more likely to make a mistake.  Then we'd have to do it again.  And again, and again.  Eight rounds in total.  From my altercation with Mannequin, I knew we wouldn't make it through even the first few encounters without some loss, some injury or casualty.  By the time the eighth round of testing rolled around, what kind of condition would we be in?  What condition would my territory be in?



I'd initially seen Tattletale's deal with Jack as a good thing, a miniscule chance at success, with some drawbacks and negative points.



The more I dwelled on it, the more daunting it seemed.



``You okay?'' Grue asked me.



``A little spooked,'' I admitted.



He set a hand on my shoulder.  ``We'll make it.''



Speaking from the perspective of someone who had gone toe to toe with these guys, I wasn't so convinced.





