
``Aisha's not here,'' Grue informed us.



He locked the door to his headquarters and climbed on top of Sirius.  Bitch and I were astride Bentley and Lucy, respectively, and Bastard was on the end of a chain that Bitch held.



``Did you give her a job before you left for Coil's this morning?'' I suggested.



He shook his head, ``No.  I make notes, and I make \emph{her} take notes too.  Keeping track of that girl is a nightmare.''



``Tattletale's working on her idea,'' I said.  It felt ineffectual as reassurances went.  In the hopes of elaborating on the thought, I added, ``Maybe she'll be able to keep track of Imp and stay in touch with us, to keep us informed.''



``Maybe.  You done a sweep of the area?''



I shook my head.  ``Need another minute.  I'm trying to be thorough in how I check each area for enemies, and Mannequin can see my bugs, so I have to use silk lines to try to catch him.  It's slow, and I definitely don't want to miss him.  Also, it would be nice to grab some bugs to build up and replenish my stock.''  I let bugs gather on Lucy's back, depositing spiders and large beetles.  The dog didn't seem to mind.



``Right.  Good.''  Grue looked at Bitch, ``We'll finish checking out my territory, stop in yours to help you with whatever you need to do for your dogs, then we'll pass through Tattletale's area on the way back to Skitter's.''



``I don't really care,'' Bitch said, looking off into the distance.  I was pretty sure she was deliberately looking away from me.  It was as though she wanted to pretend I didn't exist.



Grue looked at me and shrugged.



This wasn't going to work.  She was too distant, and that was dangerous.  Not that it wasn't risky to try to address the problem.  It still needed to be done.



Making sure Bitch wasn't looking, I tapped two fists together and then pointed at her.



He shrugged again.  He didn't get it?



Drawing from the bugs I had stored in my costume, I drew out words in the air with the bugs flying in tightly controlled formations.  `Confront her'.



He hesitated.



`Be leader,' I wrote.  Then I changed the words of `leader' to `honest'.



``Bitch,'' Grue spoke.



``What?''  She snapped her head around to face him.  Her eyes flicked over to me and narrowed slightly before they returned to him.



``This whole thing with you not talking?  It's not working.''



``So?''



``So cut it out.  Or at least explain what's going through your head.''



``What I think is my business.''



``No,'' I cut in.  I couldn't help it.  ``You're a member of the team, and if you're thinking about joining the Nine, then that matters.''



``I'm not!''  She snapped.



``But?'' I added.



``What?''



``You're not thinking about joining them, but\ldots?'' I let the question hang for a second.  ``\emph{Something} is eating you up.''



``Did you not hear what I said about my thoughts being my business?''



``Bitch,'' Grue warned.



``What?''  She clenched her fist, and I think the dogs could see something in her body language, because they tensed too.  She said, ``Fuck it.  Pisses me off when you get on my case.  Leave me alone.''



She kicked Bentley lightly in the sides, and the dog began walking.  She kicked him again, and he started running.



Lucy and Sirius \emph{wanted} to follow, so it thankfully didn't take much effort to get them moving.  Bitch wasn't riding as fast as she could, so it was clear enough that she wasn't trying to escape.  She wanted space, and she was angry.



I glanced over my shoulder at Grue.  How the hell were we supposed to handle this situation?



My phone vibrated at my back, and in my effort to avoid falling off Lucy, I wasn't able to get at it.  I fought to make her obey me and stop by pulling on the chains and wrenching her right, then left.  She finally halted, and I took the opportunity to grab my phone.  I'd missed my window.



It started vibrating again.



``Yes?'' I answered.



``You guys busy?'' Lisa asked.



``Just patrolling our territories to make sure that the Chosen aren't up to anything,'' I said.  A droplet of water fell on the lens of my mask.  I looked up at the overcast sky.  \emph{Rain}?



``Listen, you know that I've got some people working for me, passing on info, right?''



``Sure.  Bryce is one of them, right?''



``Right.  Well, I've got all of them keeping an eye out for capes and known faces.''



``Known faces?  Like the members of Empire Eighty-Eight who were outed?''



``Like them.  Or Jack, or Bonesaw.  But that's not what this is about.  Senegal just dropped by Coil's base, and he's passing on information from one of my scouts.  They saw Panacea at one of the shelters in Ballistic's territory.''



``I'm not entirely sure I follow.''



``All of New Wave live southwest of the Towers, the nice part of downtown.  Neither of their houses were hit by the worst of the waves, and none of the Chosen or Merchants are stupid enough to attack them, and they wouldn't succeed if they were.  You following me, now?''



``Sort of.  You're wondering why she's \emph{there}.  She could just be there giving medical help to the injured.''



``My scouts say she's keeping to herself, trying to avoid attracting attention.''



``Curious.''



``Exactly.  Want to go pay a visit?''



I used clouds of bugs to get the attention of my teammates, then waved for them to come my way when they stopped and looked my way.



``I'm not the best person to talk to Panacea.  She kind of hates me.  Remember the thing at the hospital?  The bank robbery?''



``But you \emph{have} talked to her before.  She was there to hear Armsmaster talking about you being a wannabe hero, betraying us.  If nothing else, maybe the idea of getting answers about that will get her listening so you can move on to a real conversation.''



``Maybe.  I don't really think so.  Wouldn't somebody else work better?  You guys aren't far from that spot.''



``Who would you send?  Sundancer and Ballistic are threatening by their very nature.  I'm not up to it, and she hates me \emph{more} than she hates you.  I wouldn't trust Bitch, Regent or Trickster to handle it, I think you'd agree with me there.''



``Genesis?''



Lisa sighed.  ``We could send Genesis.  Is she with you?''



``She's resting.  Or at least, she's recuperating from using her power.  If something comes up, she told us to call her, and she'll have one of her creations with us in a minute.''



``Your call.  The Travelers seem decent, but they're hiding something, and I really do think you'd be a better person to talk to her.''



``Okay.  Text me the address.  I'll ask the others and we'll call Genesis in if necessary.''



``Cool.''



I hung up.  Grue and Bitch had already returned to me.



``What is it?'' Grue asked me.



``Panacea's in a shelter, and she shouldn't be.  Tattletale finds it strange, and I agree with her.  She wants us to check Panacea out.''



``\emph{Why}?'' Bitch asked.  ``None of our business.''



``It could mean answers.  We're looking for a sixth candidate, and we can't \emph{protect }candidates like you if we don't know who they are.  Maybe Panacea is the sixth, maybe someone she knows, like Glory Girl.  If nothing else, I can raise the subject of whatever plague Bonesaw has that's supposed to scare the candidates and the local heroes into playing along.''



``It also means I have to wait before I check on my dogs and the rest of my territory.''



Grue looked my way.  Should I capitulate and tell her that we could send Genesis, to give her what she wanted, or would it be better to get her to agree, and risk angering her?  As odd as it might be, I gravitated toward the latter option.  Bitch responded better to firmness.



``She's supposedly in Ballistic's territory, which is close.  Five minutes there, up to five minutes to talk, five minutes to get back,'' I said.



``Fifteen minutes out of our way,'' Grue said.  ``And anything we find out about the Nine or their candidates can potentially help \emph{you}, Rachel.''



She scowled.  ``Whatever.''



I took that for assent and turned Lucy around.  With a shout, I got her moving.  I kept the phone in one hand while I rode, waiting for Lisa's response.



It didn't matter.  She found me before I found her.  Or, to be more specific, she found my bugs before I found her.  There were enough flies in the city that most people didn't give a second thought to one landing on them, especially if it landed on their clothing.  I habitually used my bugs to check people nearby for weapons or masks, and when I checked the people in a building three blocks away, one of the bugs brushed against Panacea.



She must have been able to tell it wasn't an ordinary bug.  As she'd done at the bank robbery, she used her power to scramble them and force whatever mechanism my power activated in their systems into a feedback loop.



Before it could incapacitate me and my power, I swept up the bugs with larger dragonflies and flying beetles and promptly murdered them, feeding them to other bugs in the area and pulling them apart.



Panacea was waiting in an alley when we arrived, arms folded.  Her brown hair was tucked underneath an army green mosh cap, the brim pulled low.



She looked exhausted, worn out.  She had that same devastated look in her eyes that I had seen in her cousin and aunt on the day of the Endbringer attack.



``I see you've got the two other horsemen of the apocalypse with you.  Where's number four?''



I shook my head.  ``Horsemen of the apocalypse?''



``Nevermind.''



I hopped down from Lucy's back.  ``I just want to talk.''



``I can't outrun those dogs, you've got me outnumbered and you've probably got more weapons than me.  I think you're in a position to do whatever you want.''



``Good,'' I said, ``Because like I said, I just want to talk.  I could get rid of my weapons if that would make you feel any better.''



``It wouldn't, really.''



I saw her step back a little, and I could tell she was ready to bolt.  We were in a position to catch her, for sure, but it would be more detrimental than anything.  If we chased her down, any dialogue I had with her afterward would be an interrogation, not a conversation.



``Okay.  Grue, Bitch, you want to give us some space?  Stay close enough that we can hear each other with shouts?''



``Sure.  You checking the area?''



``Yeah.  No trouble yet.''



He nodded and the pair of them led their dogs away.



``What's going on?'' Panacea asked.



``That's what I was going to ask you.  Why are you in a shelter, Panacea?''



``Don't call me that.''



I raised my hands a bit to stop her.  ``Okay.  Why are you in a shelter, \emph{Amy}?''



``Why is that any of your business?''



``Because two of my teammates were picked by the Nine, and Jack Slash just started a messed up version of Survivor, with the candidates as the players.''



``Survivor?''



If I'd been pressed to say, I would have said her body language shifted fractionally on hearing that.  Concern for herself?  Her sister?  Someone else?



``They didn't give you the info?  You didn't get a paper with a list on it?''  I asked.



``I was staying somewhere else last night, I heard from a classmate that my aunt was supposedly looking for me.  So I legged it.''



I could have pressed for more details there, but I suspected she'd keep to the conversation better if I gave her the info instead of demanding it.  ``They've set themselves a time limit to test and eliminate the six candidates.  Their goal is to test the candidates and kill the ones who fail, until there's only one.  \emph{Our} goal is to save them.  So when Tattletale figures out you're here instead of with your family, and when we know that the sixth candidate is apparently a hero, it gets our attention.''



``Who- who are the other candidates?''



``Regent, Bitch, Hookwolf, Armsmaster--''



``Armsmaster?''



``Yeah.  Though it might be like Cherish is doing to Regent, more to screw with him than for legit reasons.''



``Ok.''



``I can see it, though.  I've interacted with him.  He really did cross the line during the Endbringer attack.''



``And the fifth?''



``A non-cape.  I don't know the details, but she's in a secure location.''



Amy fidgeted.  ``I'm getting out of here.''



``Where?''



``Away.  I don't want to be a part of any of this.''



``You can't leave.''



``Why not?  I can find a place to hole up and hide until it blows over.''



``So long as you're in Brockton Bay, they've got someone who can watch you.  Can watch any of us.  She reads emotions, and apparently uses them to find us from half a city away.  It's probably how they found the candidates in the first place.''



``Then I'll leave the city.  I was going to anyways.''



``Fuck, I wish I still had the list.'' I muttered.  At a normal speaking volume, I said, ``No, you can't leave town, either, because Bonesaw prepared a plague or something.  If you \emph{are} a candidate and you leave the city, they'll use it.  They \emph{explicitly} said they were using it as an incentive for the two heroes that they picked as candidates.''



``Heroes,'' Amy muttered.  ``Right.''



``\emph{Are} you a candidate?''



She fidgeted again.  ``Bonesaw nominated me.''



``Do you know why?''



Bitterly, she said, ``Why do you think?  She thought I'd be a good fit.  And because my powers complement hers.''



A good fit?  ``Just based on my interactions with you, I wouldn't have thought.''



``No?'' she asked, sarcasm in her tone, ``Why wouldn't you have thought?  You heard what Tattletale said.  I'm the daughter of a villain.  I haven't been nice, I haven't been merciful, or forgiving, or considerate.  Instead of giving you a second chance, I was spiteful, I toyed with your feelings, and things spiraled out of control.  You know how much trouble that caused for my family?  The director of the PRT and Legend and Miss Militia were all at my house, lecturing \emph{all} of us about how serious these events were and how sensitive relations between the various factions were.''



``I\ldots I don't want to strike a nerve, or say the wrong thing.  I'm not very good at picking the right thing to say.  But I forgive you.  I know you were tired.  You were overworked.  You had no reason to like me or to do me any favors.  And you healed me anyways.''



I could see her tense.  Would she storm off?  Lash out at me like Bitch would?



She just fell silent, avoiding eye contact with me.



``I don't think you're a monster,'' I said.



She laughed briefly, and it was a dark utterance with no humor in it.  ``No?''



``Everyone knows how you visit hospitals.  How many people have you helped over the past three years?  How many lives have you saved, how many people have you rescued from a lifetime of misery?''



``I hated it,'' she said.  ``It was such a burden.  So many long hours spent around sick people, and I got numb to it, I stopped caring.  Do you know how many hours I've spent awake at night, wishing my powers would just go away, or that some circumstance would come up where I'd make some excusable mistake where they would eventually forgive me, but where I couldn't visit the hospitals anymore?''



It caught me off guard, hearing it, but I managed to get my mental bearings.  ``You didn't ask for your powers.  I'm sure even doctors get worn out, they hate their job, they have bad weeks.  Except doctors have fellow staff members, they have friends and everything to go back to, and they're \emph{adults}.  You're still a teenager.  You started doing what you were doing at a time when most people didn't.  You didn't have the maturity and the defenses against the pain you were seeing that doctors pick up over the course of the first twenty-five years of their lives.''



She shook her head.  ``Don't.''



``Don't what?''



``Don't make me out to be a good person.  Bonesaw has a better idea of who I am than you do.  Maybe I wouldn't have thought so, three days ago, when she first met me, but then I fucked up.  I proved her right.  Every fear I had about being like my dad came true.''



I didn't have a reply to that.  I couldn't pry, and I couldn't elaborate.



``So you're the supposedly good person who was pretending to be a crook, and I'm the monster who was pretending to be a hero, but when the dust settled, we both wound up being villains.  Funny how that works.''



``Maybe because doing the right thing is hard,'' I offered.



She shrugged.



``But you \emph{can} do the right thing.  We need your help.  I don't know your circumstances for leaving home.  I won't pry.  But I think you're one of the few people who can stop Crawler, maybe even Siberian too.  We need you around in case they start winning and we wind up with injuries or death, and we need you in case \emph{we} start winning, and they decide to use that plague out of sheer spite.''



``More burdens, more pressures and demands,'' she said, her voice quiet.



``Yeah.  That's the way things play out.  But we can help to protect you in exchange.  You watch our back, we watch yours.''



``I don't know if my conscience can handle taking that final step over to the dark side.  Or if I can handle being in Tattletale's company.''



``We're operating as two distinct groups.  Tattletale's with Regent and most of the Travelers.  It's me, Grue, Imp, Genesis and Bitch here in the north end of town.  Absolute--''



I didn't finish my sentence.  Something constricted around my throat, fingertips digging into the windpipe, and the air ceased to flow.  I struck behind me, hoping to catch my attacker, but there was nobody there.



I realized what was happening too late, when my feet were hauled off the ground.  In the span of a second, I soared up six or seven stories, the counterweight to a nine-foot tall man in featureless white armor who plunged downward to land in a heap on the ground.



\emph{Mannequin}.



He'd repaired himself this fast?  Did he have spare parts lying around?



I reached up and tried to wind my arm, wrist and fingers around the chain, to alleviate the pressure on my throat, and to give me a grip in case he decided to let go.



Mannequin hauled himself to his feet and the chain that stretched from his arm to the rooftop and back down to me made me bounce with every small movement.  He advanced on Amy, who backed away.



I had to do something.



Calling on the bugs that had covered Lucy, I stirred up a cloud to grab Grue and Bitch's attention, then pulled all of the bugs into the alleyway where Panacea and Mannequin were.



The way I was hanging, with Manneqiun gripping my neck from the back, I had a vantage point to witness what came next.  If my bugs weren't enough of a signal to the others, Amy's scream of pain was.  Mannequin caught up to her and plunged a knife through her hand, pinning it to the wall.



He left her like that, in enough pain that she couldn't stand, but unable to drop to the ground because her hand was impaled.  Turning, he faced the incoming stampede of Grue, Bitch and the four dogs.



While I struggled to escape, drawing my knife with my free hand while gripping the chain with the other, I sent my bugs in to assist.  Same tactic as last time.  My bugs drew out lines of silk and plastered them around him.  I focused on his free hand and his legs, aiming to hamper his range of movement.



Something was different from last time.  I wasn't sure if I would have known just going by the naked eye.  But I knew almost right away by the lengths of the silk I was drawing around him.  His arms were bigger, and the weight of them was making his body hunch forward a fraction.



I tried to scream, to call out a warning, but I couldn't \emph{breathe} to do it.  I would have used my bugs to draw words, but the pair were moving too fast to read anything I threw their way.  I drove the knife at the hand that held me instead.



Bitch ordered Bentley to pounce, Mannequin raised his arm, and the deafening boom of a gun firing filled the alley.



The shot was powerful enough that Bentley was knocked off course.  Mannequin simultaneously leaped and retracted the chain that still stretched to the rooftop, swinging across the alley and escaping collision by mere fractions of an inch.



Bentley and Bitch sprawled on the ground.



I hacked at the hand that held me again while Grue threw darkness over the pair of them.



My swarm-sense gave me a picture of what happened next.  Grue dodged to one side, and Mannequin followed him, his arm unerringly moving to follow his target.  My bugs were then blown out of the air as another shot was fired at Grue and Sirius.  I could feel it spread out, hitting multiple points on the pair of them.  A shotgun?



Lucy pounced from where she'd been moving in Sirius' wake, and she landed half-on top of the chain that held me.  I surged another three or four feet up, and the hand caught where it fixed on a loop of metal that had been sunken into the corrugated metal of the roof.  This was where the chain was threaded.



I hacked at the hand again, while gripping the metal loop.  The knife caught inside a joint, and I worked at it, trying to bend it or pry the joint apart.  I couldn't really see what I was doing, and the bugs I had on the surface of the hand weren't as useful as I'd hoped.



Below me, Lucy and Mannequin fought, the smaller Bastard dancing around the edges, trying to find an avenue for attack, or hampering Mannequin's movements.  Lucy managed to get on top of him.



A third gunshot sounded.  There was a long pause, where nothing and nobody moved, and then a fourth gunshot.  Lucy slumped over, crashing on top of Bastard.



Mannequin stood, taking a moment to use a knife to cut at the threads that wound around his arms and legs.  When he was done, he disconnected the chain that ran to the hand that held me aloft.  I was left hanging from the metal ring.



He watched me for several long seconds, his head raised.  He abandoned his grip on the back of my neck, and his arm dropped into his waiting hand.  The chain fed through the metal loop, running over my fingertips, before it was gone.



A few seconds passed, and I realized he was still staring up at me, one finger pointing at me.



Me?  He wanted something from me?



No, he turned away, striding past Amy, who was still impaled to the wall by her hand, and stopped when he stood over Bitch.



Drawing another knife from a point I couldn't see on his body, he stabbed Bentley in between the eyes.



He turned to look at me one last time, and then he was gone.



My hands were tired from riding the dog, and while my gloves afforded me some traction on the metal loop, the fabric seemed to slide under my sweating fingers.  I tried to haul myself up enough to get one leg over the edge of the roof, and nearly lost my grip.



My hands wouldn't give me enough of a hold, and I didn't trust my knife to bite deep enough into the concrete to serve any better.  I let it fall and raised my other hand to the metal to get a better grip.



Again, I tried to swing one leg up.  This time I got it over the roof's edge.



I ran pell-mell for the door that led into the crowded building below me, using bugs to get the general shape of the hallways and find my way.  Some people shrieked as I ran into and through the crowd, out the front doors and back to the alley.



Grue was standing, pulling the knife free from Amy's hand so she could slump to the ground.  Bitch knelt on the ground beside Lucy, while Bentley lay on the ground, the knife still embedded in his skull, and both Sirius and Bastard hung back, limping as they moved, blood leaking from a dozen dime-sized wounds in their flesh.



A low growl tore free from Bitch's throat.  But I knew before I looked that Lucy hadn't made it.  Two shotgun blasts directly to the chest cavity.



I didn't know what to say.



``You led him right to me!''  Amy accused us, sounding more than slightly hysterical.



``I\ldots he slipped past the silk tripwires I put around the area.  And they can find you,'' I said, the words clumsy, made worse by my sense of disorientation over the surprise attack and the distraction of the pain in my neck.  ``Anyways.  They can find you anyways, with Cherish.''



``My hand.  Hurts,'' Amy said, ignoring my fractured explanation.



``Heal yourself,'' Grue said.  He wasn't looking at her.  His attention was on the knife he'd pulled from her hand.



``I can't!  I'm immune to my own power.''



``Calm down,'' he said.  ``Panic won't get us anywhere.''



``Fuck you!  Fuck you all!'' Amy said.  Then she ran.  I didn't have the air in my lungs or the heart to chase her, and both Grue and Bitch were too hurt to give chase.  I could run and catch up, sure, but what would I accomplish?



For now, it was better to be here, with my teammates, and make sure they were okay.



``She's dead,'' Bitch said, quiet.



``I'm sorry,'' I replied.  ``We'll get them, okay?  We'll fuck them up.''



She looked at me, and the anger and hatred that had colored her expression before was gone.  She looked forlorn.



Grue handed me one of the knives, then handed one to Bitch.



It was short, only four and a half inches long, and there was a word inscribed on the steel with a smoky texture, so the six large capital letters and the row of smaller characters were pale against the gleaming, bloodied steel.



CHANGE.
2200/2012164



``Bitch has her deadline for her test, and Amy does too.  Ten in the evening, and I think it's for tomorrow.  Jack said his test always involved someone changing themselves in a way that costs them something.''



``I'm going to kill him,'' Bitch growled.  ``Fucking tests.  Killing Lucy, stabbing Bentley.''



A minute passed as we pulled ourselves together, checking our injuries.



``He left me alive,'' I said, as the realization dawned on me.  ``He didn't kill any of us, but he had an excuse and the ability to kill me.  Why didn't he?''



``The world revolves around you, doesn't it?''  Bitch snapped.



I was trying to think of how to reply to that when the thought struck me.  The world, my world.  \emph{My people}.  Mannequin had been nearby when I was in my territory.



``He's going to hurt me by going after my gang.''





