





How the hell was that motherfucker that fast?



He wasn't even trying to avoid my bugs, so I had a sense of where he was as Grue, Bitch and I tore down the street on our dogs.  I rode behind Grue on Sirius, my arms on his shoulders, while Bitch rode Bentley, Lucy's corpse lying across her lap.



We'd lost a couple of minutes as we helped Bitch retrieve Lucy's real body.  It was eerie to see.  When the dogs grew, they really appeared to be adding mass, literally growing and stretching.  Somewhere in the transformation, after they weren't recognizable as the animals they had once been, their real bodies were reformed inside a placenta-like sac.  Mannequin's gunshot had opened a hole in Lucy's chest and penetrated that membrane to kill the real dog within.  We'd used my knife and Grue's raw strength to help pull the dog free in a grim sort of anti-childbirth.



It might be seen as a waste of precious time in a crucial moment, but I doubted we would have had Bitch in our corner otherwise, and without her, we wouldn't have a ride, so to speak.



I'd consoled myself with the fact that we had a pair of massive, muscular steeds that could outpace any car you'd see on the street, and Mannequin was limited to his two legs.  The thing was, somewhere around the point where he stopped trying to evade my tripwires and my bugs and picked up speed, when he really started \emph{moving}, I realized he was actually faster than the dogs.



Mannequin covered a lot of ground with his long legs and seemingly endless energy, and he didn't have any injuries.  The dogs, Bitch and Grue did.  Mannequin had been aiming at the animals more than he'd aimed at Grue or Bitch, so the damage to my teammates was more or less limited to a few flecks embedded in the legs, buttock and feet.  The injuries were small, but one in Bitch's stomach worried me.  There were way too many vitals that could be hit with that location, and it was bleeding worse than any of the others.



She wanted to press on, and I wasn't about to try and change her mind.  I wouldn't be able to stop her, for one thing, and I \emph{did }want to help my people.



Mannequin moved in a straight line, onto rooftops, down to the ground, or halfway down and through windows that had been stripped of glass, emerging from the far side.  My bugs swarmed him where I could get them to, trying to snag him with lines and threads of silk and hamper his movements, but I could only get him with a small few at a time.  He was approaching the edge of my effect's reach, and I knew I'd lose track of him shortly.



Once I did, I wasn't sure I'd catch him again.  He could apparently see my bugs and since our last confrontation he'd gained the ability to see the spider silk I was placing on him or in his vicinity.  It was remarkably high-resolution vision for someone who hadn't been able to notice that I didn't have a pool of blood spreading out beneath me during our last fight.  Or was his inability to see that \emph{because} he was calibrated to see the small things?



It wouldn't matter if I couldn't find him or catch up to him.



``He's veering left!'' I shouted to my teammates, ``Faster, Sirius!  He's getting away!''



I could feel a tremor in Sirius' body, like the momentary tremor of a twitching muscle, but in every muscle.  My legs spread a fraction further apart as he grew larger, his ribs expanding further in either direction.  The increase in his speed was small but noticeable.



I cast a glance over my shoulder at Bitch.  Her mask had fallen off at some point when we'd been retrieving Lucy or during our ride.  She looked drawn, the lines of her mouth and the bones of her face that much more prominent.  Had I failed to notice she was like that before, was it pain from her injuries that did it, or was it anger?



Whatever it was, I suspected this use of her power was drawing on reserves she didn't have.



Mannequin disappeared into the penthouse floor of an apartment building, and I positioned bugs at the very periphery of my range to prepare lines of thread and to gather so they could land on him as he emerged.



Somehow, I couldn't say how, he emerged from a \emph{lower} floor, mere seconds after he'd entered the building.  He brushed past a small handful of insects, and then he was out of reach of my swarm.



``He's out of my range!'' I shouted.



Nobody responded.  I had to double-check that Bitch hadn't fallen from Bentley's back.  She didn't look any better than she had a moment ago, and she looked out of breath.  I expected the pain of her injuries was taking its toll.  As for Grue, I couldn't really see anything but the back of his head and his shoulders while I clung to his waist.  I didn't get the sense that he was about to pass out, either.



No use in responding when you couldn't spare the breath and everyone knew what the answers would be.  We'd search for him at the last place we'd seen him.  My territory.



Giant paws pounded on the wet pavement as we raced for our destination.



How the hell were we supposed to fight him?  If we could even find him?



He'd have some countermeasure for my bugs and my cocoon strategy.  There was no way he'd let himself get caught up in the same trap twice.  Grue's power didn't affect him.  Bitch's dogs did affect him, but they weren't bulletproof.



That was without factoring in any additional weapons he had.



One arm around Grue's waist, I drew my phone from my utility compartment and dialed Genesis from my contact list.



``Genesis here.  What?''



``Mannequin en route to my territory for some kind of revenge against me for our last fight.  How fast can you pull a body together?''



``Two minutes.''



``He'll be there in five.  Clear people out of the way, and put together a form that can take a beating and hamper him.''



``On it.''



Sierra was the first and only contact I'd entered into the phone beyond the ones Coil had put in prior to giving them to us.  I contacted her next.



``Sierra here, boss.''



``Clear people out of the area, and contact everyone you gave a phone to, telling them to hide and take cover.  Mannequin's coming back to make trouble.''



``Got it.''



I hung up.  With the jostling movement of the dog's running, I didn't trust my ability to put the phone away in the compartment, so I held it in one clenched fist.



During the six or seven minutes it took us to cross from Ballistic's territory to my own, my teeth were clenched so hard I thought I'd break something, my neck and shoulders so tense they felt more like stone than flesh.



I valued my ability to come up with answers, but my mind was empty.  I wasn't sure how I'd deal, and the worst part of it was that it wasn't me that was necessarily going to pay the price.



As we entered my territory, I felt strangely composed for the anxieties that tore through me, a little detached from things.



My bugs swept through the territory, and I did my best to recall where tripwires had been set and figure out which had been broken.  I checked on my people, using bugs to make sure they were standing and that they were somewhere safe.



Could I sweep through my territory using squadrons of flies with dragline silk stretched out between them, to the point that he couldn't slip past them?  It would take time to set up.



No.  There was no need.  As I approached the heart of my territory, near my barracks, I found him, standing in the middle of the road.



``There!'' I called out to my team.  We changed direction and charged toward the street in question.  We stopped when he came into our view.



Mannequin stood in the center of the road, his back to us.  Half a dozen of my people were lying on the road, unconscious or dead.  I couldn't see any blood.  There were a couple more people in nearby buildings that had fallen as well.  How had he reached them?  Why hadn't Genesis and Sierra been able to get everyone out?



A quiet horror ran through me like ice water.



Genesis, too, was on the road, in the process of dissolving.  She'd taken on the form of something like a stegosaurus crossed with a scorpion, all brawn and armor plating, with a long, prehensile, wickedly spiked tail.  He'd beaten her.



Very little of the silk I'd laid on him was still intact.  My bugs settled on him, and began to draw out more silk, binding him.



He turned our way, and his mouth opened like a ventriloquist dummy or a christmas nutcracker.  It jiggled up and down, silently, mocking.  Laughter without sound.



``Fucker!'' Bitch screamed.  Then she whistled, with a volume and pitch that could make crowds stop in their tracks.  Bentley charged.



The bugs I had on Mannequin began to die.



That took me a precious second to process.  ``Bitch!  It's a trap!''



She turned to look over her shoulder, and Bentley took some cue from that, because he turned slightly.  Maybe that helped, because she hauled him into a hard left turn, wheeling around.



Whatever it was that Mannequin was doing, it spread fast, knocking my bugs out of the air and reaching out past Bitch and Bentley before they realized the threat and started running \emph{away} from him.



``Get back!'' I shouted.



Bitch urged Bentley into a run.  They made it four steps before Bentley collapsed.



Tumbling to the ground, Bitch landed and couldn't sustain her own weight with her injured leg.  She landed flat on her stomach, and then began making retching sounds as she gasped for air and continued to crawl forward.



Mannequin's mouth continued jittering up and down, and he took a step closer to us, his hands upturned at his sides.



\emph{Gas}.  Colorless, scentless, swift to spread and it incapacitated in seconds.  If my bugs were any indication, it also killed its victims shortly after.



I looked around, hoping and praying for some sort of outside assistance.  Nothing.



It was down to me, Grue, Sirius and Bastard.



Bastard looked unnerved.  His master and alpha were out of action.  He took a step forward, then back.  He was unnerved by Mannequin, and I suspected he could smell the gas.



``Bastard!'' I said.  He whipped his head around to look at me.



\emph{Here's hoping that Bitch trained him well.}



``Get your master!  Go!  Fetch!'' I pointed at Bitch.



Bastard turned, started forward, and then stopped.



``Go!  Fetch, fetch!''



He bolted.  Mannequin continued walking slowly towards us.  He didn't move as Bastard approached and picked Bitch up by the back of her pants.



It would be so easy for him to simply shoot Bastard and slow him down long enough for the gas to take effect.  He didn't.



``Bastard, come!  Come on!''



The puppy ran back to us.  There was nothing we could do for Bentley.



I hopped down and grabbed Bitch as Bastard came back to us.  He growled as I approached, but he didn't protest as I took Bitch into my arms and dragged her back toward Grue and Sirius.



Grue didn't dismount, but I doubted he would have managed well if he had, given his injured leg.  I tried to ignore Mannequin's steady approach as I propped Bitch's limp form up against Sirius' side long enough to lift her arms up to Grue's waiting hands.  Together, we hauled her up so she was lying astride Sirius' shoulders, just in front of Grue.



``Gas,'' I muttered.  ``There's a cloud of gas around him.''



``Fuck me,'' Grue said.  ``I'd hoped we could at least hit him.''



I looked at Bastard.  Too small to ride.  He was the size of a pony, but he wasn't built for riding in the same way, and the spikes and bony plates that covered him were too densely packed for me to find any sort of flat patch to sit on.  I reached for the chain that trailed from his muzzle.



He growled again, vicious.



I was taken aback for half a second.  Then anger set in.  I barked, ``Enough!'' and I snatched up the chain.



He growled again, and I hauled on it.  The way it was rigged, it looped around his snout so it would tighten around the end of his nose when the chain was pulled.  It was like a choke collar, but focused more on the sensitive snout than on the throat.  He recoiled and tried to pull away, and I tugged again.



This time, he went still, resisting less.



``You're with me, puppy,'' I said, pulling on the chain as I backed away from Mannequin.  ``Grue, take Bitch and get to cover.  I can't see inside your darkness so long as that gas is wiping out my bugs, and he isn't bothered by it, so remove it as fast as you apply it, but try to push the gas away or displace it or whatever.''



``We need a plan to \emph{win} this,'' he said.



``Priority one is surviving until we think of one,'' I replied.  ``Genesis will be back in action in a few minutes.''



``A few minutes is a long time.''



``I know,'' I looked at Mannequin again.  He'd closed his mouth and was standing still.  I pointed.  ``You go that way, I go this way.  Keep an eye on the sky.  If there's trouble, we signal each other.''



He nodded once.



``Go!''



We split, and Mannequin broke off, chasing Grue.



I headed the opposite way.



\emph{Think, Taylor, think!}  Mannequin was a smart guy.  Everything he did would be calculated to achieve some specific goal.



Why was he here?  He wanted to hurt me.  He wanted to hit me where it hurt, and he'd done it.  He'd killed no less than ten of my followers.  Charlotte and Sierra could easily be among them.



He had let us find him because he wanted to bait us into a trap.  It had worked against Bitch, for the most part.  She wasn't dead, I hoped, but she was out of action.



What about the small stuff?  The little things?  After he'd caught Bitch, he hadn't shot her, and he hadn't shot Bastard when the puppy was making its rescue attempt.



Why?



He could have been conserving ammunition.  What was that term for `the simplest answer is often the correct one'?  It didn't matter.  It was possible.



I moved my bugs closer to Mannequin, to test his presence for gas.  Only a few perished.  There wasn't much, if any.  His mouth was closed.  He was catching up to Grue.  Grue must have noticed, because he directed Sirius up into an alley and towards a roof.



Mannequin stopped and raised one arm, then fired.  My bugs felt the concussion of the shot, but no reaction from Grue and Sirius.  There was a pause, then another shot.  Again, no reaction.  Two misses.



Okay.  So Mannequin was shooting now, when he hadn't been before.



Were there other clues?  What had changed after he'd closed his mouth?



He'd started running, for one thing.



So he hadn't been running, he hadn't been shooting\ldots  What had been holding him back?  It could have been him trying to look intimidating, but he could have achieved the same ends by shooting Bastard and making me watch Bitch die.  He could have been just as scary running towards us as fast as he'd sprinted from the ambush site to my territory.



The gas.  If the gas was coming from his mouth, and he was being careful in how he moved, that meant there was something about the gas.  I even had an idea about what it was.



Maybe he hadn't wanted to blow himself up.



He'd been invested in terraforming, once upon a time.  Making inhospitable environments hospitable.  Chances were he was loaded down with custom-made organisms that were primed to generate the gas he was using, maybe even storing it in a compressed form.  Given his tinker abilities, they could be advanced enough to account for the sheer volume of the gas.  It could even be how his guns operated: with compressed, combustible gas used to fire the shot.



There was no way to say for sure, but my gut told me I was right or I was pretty close to the mark.  His actions, both the obvious and minor ones, make a complete, logical sense if I assumed he was spewing out massive volumes of flammable gas.



Could I even take advantage of that?  The amount of gas he seemed to be putting out would make for a devastating explosion.  It could potentially hurt him, but I couldn't say if the shockwave or the blast itself would kill me or any nearby innocents.  If there was enough gas, it could even damage or destroy nearby buildings.  Some of the structures around here weren't exactly sound.



If nothing else, it gave me a clue about what to watch for.  It also gave me a last-ditch weapon if things \emph{really} went south.  I ordered my bugs into the building I'd designated as my people's barracks and collected some small items with silk and clouds of bugs working in unison.



A spear of darkness soared towards the sky.  When it lost momentum, it began billowing outward and drifting slightly with the wind. A signal.



``Come on, Bastard!'' I ordered.  I bolted for Brian's location.  I crossed the street, glancing at the fallen Bentley, and I headed toward an alley.



My bugs crossed paths with me, and the items made their way into my hands.  A cheap plastic lighter and a packet of matches.  I stashed the matches between my belt and my hip and slid the lighter into a small pocket in my utility compartment.



I really hoped I wouldn't have to use them.



Entering the alley, I swept through the area with my bugs, directing them to extend outward with lines of silk between them.  They were gathered close enough to one another that Mannequin wouldn't be able to avoid them.



I found Mannequin and the black smudge of Grue's form at the opposite end of the alley.  Sirius and Bitch were a distance away, both sprawled at the base of a building, covered in rubble.  I wondered how this scenario had unfolded.  How had Mannequin hit them that hard?  Grue had reached the roof, the last I saw, and I'd missed what came next because I hadn't wanted to lose precious bugs from my swarm by getting them gassed.  Whatever had occurred, Mannequin had turned the tables and brought them back to the ground, hard.



Mannequin looked at me, and his mouth was open, engaged in that same shuddering up and down movement as before.  I raised one hand to the fabric that covered my nose and mouth and backed away.  Were Bitch and Sirius close enough to be getting gassed too?  I could feel bugs crawling on them.  Both were breathing, though Bitch's breaths were rapid and hoarse.  My bugs were alive, as well, which meant they were safe where they were.  A quick test with my bugs told me the cloud around Mannequin was small, with a radius of about four or five feet.  There was no gas around me, either.  The bugs on me weren't suffering, and they'd be the first to die or feel symptoms.



But Grue?  Grue had surrounded himself in a thick cloud of darkness, to the point that I couldn't make out his arms and legs in the midst of it.  From what I could gather, he was getting some benefit from it, and was pushing the gas away.  How long could he sustain that, though?  Was the darkness filtering it out, or was he holding his breath, slowly suffocating?



``Mannequin,'' I said, sounding a million times more calm than I felt.  ``You're going to back off and you're going to let him go.''



He cocked his head to one side.



I raised the matchbook and, after checking again that my bugs were gas-free, lit it.  A handful of my bugs carried it into the air.



``Or I light you up,'' I said.



Could I?  I believed I could.  Maybe it was fatigue speaking.  Maybe it was the grim recognition of the fact that Mannequin had spoiled any hopes I'd had of winning Coil's respect and saving Dinah when he'd murdered the people in my territory.  He'd singlehandedly destroyed my reputation and dealt a grave blow to the thing that had been driving me forward.  Maybe a teeny-tiny part of it was hopelessness, knowing that I couldn't  beat him otherwise.



So yeah, if he was going to snatch my hopes of saving Dinah from me, if Bitch and Grue were about to die anyways, I could turn the tables and blow us all up.  I might not save Dinah, but I could save all the people Mannequin would murder otherwise in the course of his career.  No bluffing.



He stepped back, and I realized his foot had been on Grue's chest.  I watched as Grue stood and then began limping toward me.  Bastard growled and tugged on the chain I held.



I was in the process of reaching out for Grue to help steady him when I saw Mannequin move.  He closed his mouth, raised one hand, and I could see a hole appear in the base of his palm.  The barrel of a gun.



``No!'' the word was as much a grunt as anything else as it came from my throat, too choked for me to say anything normal.  I grabbed for Grue as I'd planned and I shoved him to the ground.



In a movie, that might have been the heroic sequence that occurred in slow motion, where the lunatic villain missed the pivotal shot by a hair and blew himself up in the process.  We'd be left bloody but victorious.



But Mannequin didn't fire.  He was too collected to do any of that.



He adjusted his aim, directing his hand-gun to where I'd pushed Grue to the ground.



``No!'' I said, and the sound wasn't a grunt this time.  I stepped in the way, putting myself between Mannequin and Grue, arms spread, half-kneeling.  Bastard tugged on the leash again as he stepped forward, and I almost fell on my face.  I could let him go and sic him on Mannequin, but he'd almost certainly die like Lucy had.



``Bastard, back,'' I said, tugging him to one side.  I wasn't about to let a dog take a bullet for me.



Besides, a part of me suspected that Mannequin was going to let me live so he could make me watch while he killed my friends and followers.



I stared at his blank, featureless face, praying my instincts were telling me the truth.



Then he shrugged, and my heart fell.



Three things happened all at once.  The first and most painfully obvious was that I got shot full in the chest.



The second was that I realized Grue was using his power to shroud us in darkness.  He'd probably started the second Mannequin shrugged.



The third was the explosion.



Long, disorienting seconds passed in the aftermath.  The pain hit me like a summer rain.  There was a second of nothing at all, I realized it was starting, and then I was treated to buckets of it.  I writhed, my ribs screaming in agony, trying to find some position where the pain would be less and failing.  I felt like a hot poker was being shoved into the spot on my ribs where I'd taken the hit the previous night.



``Hey, hey,'' Grue said, ``You're okay.  You're in one piece.''



I shook my head, unable to catch my breath.  Each time I inhaled, it seemed to double the pain.



``You gotta stand, T-  Skitter.  Stand up.''



More through Grue's efforts than my own, I was helped to my feet.  Every movement exacerbated the pain in my chest.



I gingerly touched the site of the gunshot.  Flecks of what looked like glass fell as I ran my hand over the cloth.  Still couldn't breathe.  The explosion had ignited every piece of rubbish at this end of the road that stood taller than the inch-high water level.  Grue and I weren't, thankfully, blazing.  My hair hadn't been ignited either, and perhaps most importantly, we hadn't been pulverized by the shockwave.  It hadn't been a \emph{huge} explosion, but it had been substantial enough.



I looked for our opponent, and I saw Mannequin virtually unscathed, lying in the shallow water.  The blast had knocked him sprawling, but he'd disconnected his parts so only lengths of chain attached each.



An application, perhaps, of that martial arts principle.  How did it go?  An oak is broken by the hurricane's winds, but the supple willow only bends?  He was already pulling himself together.  There was barely a mark on him.



``Run,'' Grue said.



I was about to voice an agreement when I saw Bastard lurch to his feet.  The chain leading to his muzzle wasn't in my hand.



Bastard pounced on Mannequin, taking one of the villain's arms in his jaws.  Clenching, he began whipping Mannequin around like a rag doll.  Twice, Mannequin's lower body was bludgeoned against the nearby wall.



\emph{Yeah, didn't expect us to be that tough, did you?}



Mannequin turned the tables in a second.  Between one of Bastard's shakes and the next, the villain stopped flopping around.  I realized he'd ejected the knives from his toes and staked them in Bastard's neck and snout for leverage.  His one free hand dangled at his side.



Moving was agony, but I was lurching towards them in a half-run before I fully realized why.  Mannequin raised his free hand and pointed it at Bastard's left eye.



I caught his arm and hauled it back in the same moment he fired.  Bastard repaid my kindness by whipping Mannequin to one side, striking me.  Both Mannequin and I fell sprawling to the ground.



No sooner had I fallen than Grue was there to help me up.  He was slower than I was with that granular buckshot in his leg, so he'd only just caught up.



Mannequin on the ground, Bastard off to one side, largely untrained with no master and nobody holding his chain, Grue and I both helping one another stand.



That vibrating mouth of Mannequin's was going again, puffing gas into the air, maybe to buy himself some breathing room from the dog.



``Bastard, stay,'' I said.  What commands had I heard Bitch give her dogs?  ``Off!''



Couldn't say whether Bastard obeyed or if he just didn't want to attack anyways.



I had to check twice to see that there wasn't anything burning in Mannequin's immediate vicinity.  No stray garbage to ignite the gas, sadly enough.



I looked behind me, and saw that the flames were raging.  Even the water's surface was on fire.  How?  Had there been some chemical nearby, or something in the gas that transferred to the water's surface?  Our avenue of retreat was shrinking.



Whatever.  I reached behind my back and retrieved two items.  The change purse was the first.  I popped it open.  A variety of quarters, dimes and nickels, all kept in place with wadded tissue, and a few small paper packets of smelling salts.



It was stupid to be carrying change around, really, but I'd wanted to have some on hand since it had crossed my mind during my first night out in costume.



I grabbed a tissue and tore it, once, then twice, until I had a series of strips.  Then I ignited them with the lighter, the item I'd grabbed with my other hand.  Dragonflies gripped the burning tissues in the instant I let them fall from my fingers.



Mannequin shut his mouth, stepping back.  Half of the tissues went out or were dropped by the burned dragonflies before they got close enough.  Which meant that the other half made it.



The gas ignited for a second time, but I didn't get to see it.  Grue shielded us with his darkness once more.  Whether it was to dampen the shockwave or keep us from being blinded by the light or something else, I didn't know.  I could only trust that it worked.  The darkness dissipated, we were standing, Mannequin wasn't.



A whistle from Bitch's direction and a signal that was too brief for me to catch sent Bastard forward.  With Bitch's condition, I couldn't imagine how she handled it, but she managed to pump Bastard up.  He grew to half-again the size he'd been, roughly as large as a small car, and when he bit down on Mannequin's arm this time, he broke the material.  He adjusted his grip until he had Mannequin's lower body and legs in a hold, but the material there proved sturdier.



\emph{Two arms in two fights,} I thought, with a grim satisfaction.  The flames at our back were getting a touch too close for comfort, so I stepped forward, supporting Grue.  His arm around my shoulder, we approached as close as we dared to Bastard's mayhem.



Sirius was hauling himself out of the rubble, with Bitch in the arch that formed with his front legs, chest, and the ground.  She stood, shaky, still breathing funny, making rhythmic facial motions like she was swallowing convulsively or gagging.



Grue limped over to Bitch's side.  She couldn't stand without Sirius's support, but Sirius was shoring up the rubble with his body.  Grue gave her the support she needed and the pair of them made their way towards us.  Sirius stepped away from the wall and the rubble he'd been holding up tumbled to the ground, and he returned to his master's side.



``Bastard,'' Grue said.  ``Monster.  Freak.''



Grue took Bitch's hand and placed it on my shoulder.  She didn't pull away.  Once he was sure we were both standing, he stepped away.  Bending down with an excruciating slowness, Grue picked up a piece of rubble that had to have weighed fifty or sixty pounds, roughly cone-shaped.



Bitch seemed to follow his line of thinking.  ``Sirius, hold!''



The dog lurched forward and placed both front paws on Mannequin's body, pinning his arm and chest. Bastard growled at the one who was intruding on his quarry, and Sirius growled back.



Bastard quieted.  It seemed he didn't fully realize that he was bigger, more dangerous and less injured.  He was too used to being the puppy, with Sirius as the full-grown one.



Grue limped around the scene until he stood over Mannequin's body.



``Ignore the head,'' I said, quiet.  ``Nothing important in there.  I'm not joking.  It's a decoy.  Get him in the chest.''



Grue nodded and hefted the chunk of rubble until it was over his head, point facing forward.



Would it puncture?  Hard to say.



Worth a try.



``Do it,'' Bitch growled, beside me.  ``Killed Lucy.''



``Bentley too, maybe,'' I said, quiet.  ``I'm sorry.  I don't know if he made it.  There was no way to save him.''



``Do it,'' she repeated herself.



Grue didn't get a chance.  An eruption of fire tore through our surroundings.  Not an explosion.  There was no shockwave, and barely any noise.  It was more like a \emph{push, }intensely hot and brief.  We were knocked sprawling, dog and human alike.  The agony in my ribs hit me worse than ever as I was knocked flat onto my back in the water and a huff of air was struck from my lungs.



``No,'' Grue said.  ``You can't interfere!''



\emph{The Protectorate?}



It would be disastrous if the Protectorate-



No.  I fixed my eyes on the scene.  Much worse than the Protectorate.



Burnscar tapped her finger to one side of her nose.  ``I won't tell if you don't.''



``You can't assist him.  They're \emph{your} rules.''



``Jack's rules, not mine.  But fine,'' Burnscar said.  Something about the tone in her voice: it sounded casual, but there was something in it that reminded me of Shadow Stalker and Sophia.  It wasn't angry like Shadow Stalker was, but it had the same emptiness.  I just hadn't really picked up on it in the past.



Burnscar gave Mannequin a hand in getting to his feet.  Cracks marred his lower body, and his left arm was a mess of cracked ceramic and pale gray organic pulp.  I heard her murmur something.



Mannequin shook his head.  Burnscar said something else.



He raised one hand, and Burnscar slapped it in a lazy high-five.



She turned towards us.  ``There.  He just tagged me in.  Forfeited his turn.''



She cracked her knuckles, and every flaming piece of debris on the street became a pillar of fire, stretching vertically for the sky.  The fire snaked over the surface of the water to cut off our avenues of retreat.



``My go.  I'm taking round two.''





