





\emph{Bad, bad, bad, bad}.



Burnscar stood with Mannequin just behind her, sporting a red shirt and black jeans, cigarette burns running down her cheeks, and a dead look in her eyes.  Bitch, Grue, Sirius, Bastard and I stood a dozen feet away, walls of flame like bonfires barring our escape routes to the rear or sides.  Droplets of rain fell all around us, making ripples on the inch-high water that flooded the street.  The air was thick with the smell of smoke.



We'd at least had time to mentally prepare for the idea of facing Mannequin.  My strategy had been last-minute, but I'd been in the right frame of mind to fight a tinker, to anticipate ambush and tackle someone with decent offensive abilities, strong defenses and a crapton of tricks up his sleeve.



Burnscar had flipped things on us; she was in a totally different ballpark from Mannequin.  If I had to guess, her offensive capabilities were top-notch, even if they didn't break the scales like some other members of the Nine.  I couldn't even guess where she fit on the spectrum of defensive ability, but she'd been with the Nine for a little while and she was still alive, so that was some indication.  And utility?  She had every trick a pyrokinetic like Lung had at his disposal and she could teleport through flames as well, opening up a mess of tricks and avenues of attack.



``Happy now?'' She asked Grue.



``Not so much.''



Burnscar's voice was flat, without humor, like an actor reading the lines from a script without actually emoting them.  ``I \emph{am} following the rules, now.  Let's see.  Trying to remember how this is supposed to go. Test you, you pass or fail, and then I kill you.''



``You only kill Bitch if she fails,'' I said.  Opening my mouth was more automatic than intentional.  The majority of my focus was on our current situation.  Options.  What avenues of attack did we have?  What about self-defense or escape?



I had my pepper spray.  My knife and baton were available too, though I doubted my ability to dish out more hurt than I suffered in an exchange of hits with Burnscar.  Grue had his darkness, and both of the remaining dogs were in okay shape.  I had my bugs, but neither my costume nor my bugs would do well against the flame.



``I can still kill tall, dark and eerie and the alien girl,'' Burnscar said.



``Bug girl,'' I corrected.



``Don't really care.  Bitch, the test is an old one, but it's good.  We don't get to do it often enough, because it requires research.  Got to do it with Cherish because she gave us the necessary info.  Wasn't very bright, but she did.  Now that she's on the team, she can give us all the info we need.''



``You talk too much,'' Bitch snarled.  ``Get to the point or go the fuck away.''



``You're going to have to face your greatest fear.  Destroy any hold it has on you with violence, blood and death.  I don't want you to just \emph{conquer} your fears.  I want you to \emph{murder} them, before anyone else can use your feelings for them against you.''  She put a special inflection on the word `murder', making it clear she was being quite literal.



I expected Bitch to say something along the lines of `I'm not afraid of anything'.  She didn't. Her eyes narrowed.



``I'm not going to fucking hurt my dogs.''



``Not asking you to.  Dogs are easy.  Replaceable.  Sure, you might cry when they bite the dust, you love them.''  The lack of inflection or emotion in Burnscar's voice made the words sound almost mocking.  ``It's sweet.  But that hole in your heart mends, time heals the wound, you get more dogs and you bounce back.''



``I think you're underestimating how much she loves her dogs,'' I said, ``A wound like that never heals.''



Bitch turned her head just enough to give me a hard look.



``I'm not saying she doesn't,'' Burnscar shrugged.  ``I'm saying the idea of losing them isn't what scares her the most.  So forget the dogs.  I'm not asking you to hurt them, maim them, murder them or anything like that.''



Bitch glanced at Bastard.  He was growling, barely audible, low and steady, and his hackles were raised.  Were they still hackles if they were mostly fragments of calcified muscle and bone spikes?



``Kill \emph{them},'' Burnscar said.  She pointed at Grue and I.



Bitch laughed, if you could call it that.  It was more of a snort, with zero humor to it.  ``That's supposed to be my biggest fear?  I don't give two shits about them.''



``You do.  They're the closest thing to a human connection you've had your entire life.  Maybe you haven't thought it out loud to yourself, but you're terrified at the idea of losing them.  You know as well as anyone else that this relationship with your team, it's like winning the lottery for you.''



Bitch scoffed.



``Sure, it's shitty as relationships go,'' Burnscar continued, ``Anyone else would find it depressingly lame.  But they're the best you'll get.  The best you can hope for, because you're fucked up.  Believe me, I \emph{know} when someone's fucked up.''



``Like I said, you talk too much.''



``They're the best you'll ever get, and according to Cherish, you're losing them.  Whatever bond you made with them, it's fucked up now.  Maybe you did it, maybe them.  Maybe both.  But it's dying a slow death, dog girl.  Rip off the band-aid and finish off these losers who aren't going to be your friends in a few weeks anyways.  Do it, and I let you and your dogs walk away.''



``Why the fuck should I listen to you?''



``Because if you say no, if you try to run or walk away, if you attack me, I'll consider your test a fail.''



``So?''



``I'll have no reason to hold back.  Your team dies, your dogs die, and you'll wish you were dead.''



``Fuck you,'' Bitch retorted, but she glanced at Grue and I, and I could have sworn I saw doubt.  Was it indecision?  The way Burnscar had framed this, Bitch either had to admit she cared about us and fight for our sake, or Bitch could attack us to secure her safety and her dogs.



I couldn't say which road she'd take, not with any kind of certainty.  My gut told me it wouldn't be the answer I wanted.



\emph{She's considering it}.



Which meant I had to take matters in my own hands.  Burnscar held the advantage, and Bitch was leaning her way.  I needed to flip things and take that certainty away from her.



I drew from the capsaicin-treated bugs in my armor compartment.  There hadn't been any point in using them against Mannequin, but they might incapacitate Burnscar.  The trick was catching her off guard.



``You're doing it wrong,'' Grue said.



``What?''



``Did you even read the rules Jack gave us?''



``Yes,'' Burnscar frowned.  ``I did.''



``Then why are you doing it differently than he did?''  Grue pointed at Mannequin.



He was buying us time, using Mannequin's inability to talk and Burnscar's less than firm grasp to throw her off her stride.  He didn't know it, but he'd also provided me with a distraction.



My capsaicin-laced bugs made their way down my back and the backs of my legs.  Near the surface of the shallow water, they spread out, sticking to shadows, the cover of burning rubbish and the darkness that swirled around Grue.



``Doing it differently?  This isn't that complicated,'' Burnscar said.



``How's it going to look if you do it wrong?  I imagine Mannequin's going to get punished for fucking up,'' Grue said, ``But he at least \emph{tried}.  If you screw up here, right at the beginning, you really think your team is going to be impressed?  No, they're going to be \emph{embarrassed}.  And I bet they'll take it out on the person who embarrassed them.''



Mannequin tapped on Burnscar's shoulder.  She turned, and he parted his mouth slightly before drawing an `x' over it with one finger.



``Mannequin says you're lying.''



\emph{Crap}.  My bugs weren't in position to attack yet.



``You really going to gamble on that?'' Grue asked.



``Yeah,'' Burnscar said.  The flames around us swelled in size.



I had no time left for subtlety.  I gave the order for my bugs to attack directly, closing the distance by the fastest and most obvious routes available.



They rose from every corner and shadow in the area, approaching Burnscar from every direction.  I directed them towards the exposed skin of her hands, ankles, face and neck.



The second they landed, they bit, stung and clawed at her.  I even felt a few touch her face.  Then I felt her move.  For an instant, I thought she had some kind of enhanced strength or speed that let her throw herself to one side like she did.  Except it wasn't her.  It was \emph{Mannequin} that moved, throwing her to one side, so she landed in the midst of a flaming pile of trash.  The bugs on her were burnt to a crisp and she promptly disappeared.



``Run!'' Grue shouted.



Bitch hauled on Bastard's chain, shouting, ``Go!''  She climbed halfway onto Sirius' back, unable to climb up higher with her injured leg.  Grue and I followed as Bastard crashed into  one of the walls of flame, sending burning trash flying and spreading out the flaming water.  Bitch rode Sirius through the break, and Grue and I hurried after.



\emph{Hot}.



I stumbled as the heat built.  I was supporting Grue as best as I was able with the pain in my ribs protesting even the slightest movements of my arm, let alone trying to support a nearly-grown teenage boy.  The heat of the flames increased.  I think we could have made it if it was just one or two steps, but it wasn't.  Five paces failed to carry us out of the flames.  We were too slow to keep up with Bastard and make use of the way he was scattering the flames for us.



I fell in the same moment we finally got free of the flames, and Grue fell with me.  There wasn't fire underneath us, but I could still feel the heat, intense, accompanied by a blinding pain.  I was on fire.  The water was too shallow to extinguish the fires as they licked around us, and even rolling in it failed to do anything substantial.



Grue smothered us in darkness.  I'd fought alongside him before, I'd been under the effects of his power countless times, but this was different.  I was hurting, I wanted to find solutions, and now I couldn't see.  I couldn't even use my swarm sense to assess the situation, because the flames Burnscar had spread around the area were limiting my bugs' movements.  Our enemies, Mannequin and Burnscar, were similarly out of my reach.  I felt a swelling panic as I thrashed, trying to immerse myself.



I felt something heavy on top of me, then three quick taps on my shoulder.  A signal?  \emph{Grue.}  I didn't fight him as he used what must have been his jacket to pat me down and splash water onto me.  I felt the water touch bare skin.



The pain and the heat continued as Grue hauled me to my feet, but the rational part of me knew he wouldn't do that if I was still on fire.  I was burned.  It hurt, but I wasn't in imminent danger from anything or anyone except Burnscar and Mannequin.



Using my power, I found difficulty at every turn.  Everywhere I sent my bugs, I encountered fire.  I felt like a blind person tapping their cane around himself to get a sense of the surroundings, encountering only danger, destruction.  A picture was gradually unfolding, and it was an ugly one.



We ran, Grue leading the way.  We fell four times.  My legs and back were burned, Grue had his injured leg, and we were running slightly downhill.  He was clutching my shoulders hard enough that it hurt, and leaning heavily on me with every other step, while my legs had none of the strength needed to support him.



When we moved past the darkness, we were standing in the midst of the shattered Boardwalk.  We half-slid and half-climbed down the ruined area to the beach, and walked over to the water's edge.  From our new vantage point, we could see what Burnscar had done.



My territory was on fire.



Grue's shadows still covered the ground levels of the area, but I could make out the tops of the taller buildings.  Not every building burned, but there were enough.  Rain fell around us, but it wouldn't matter against a blaze like that.  In the gloom, the plumes of smoke that were as thick around as any building appeared black against the light gray backdrop of gray rainclouds.



``Come on, Taylor,'' Grue said.  He tried to pull me to my feet, and I didn't move.  ``We can deal with all that later.  Right now, we've just got to get away.  We \emph{survive}.''



``Survive,'' I muttered.



I'd been prepared to die against Mannequin if it meant removing one monster from the world.  It was a pretty good indication of how much I valued my life at these days.  I'd cut ties with my dad, dropped out of school, helped get Lung arrested and started chain of events that had led to the ABB terrorizing tens of thousands of people.  I'd served as a distraction so a power-hungry supervillain could kidnap a girl and keep her drugged up in some underground cell for \emph{months}.  I'd stood by to let a man die.  I'd become a full-fledged villain.  Pledged to protect people and then let them die horribly.  Not once, not twice, but three times.



What the hell had I been thinking, wanting to become a superhero?



``Come on,'' Grue urged me.



I stood, leaning against the concrete wall that divided the beach from the street above.



``Genesis is going to be there,'' I said.  ``We need to go find her and help her.''



``We're too hurt to do anything,'' Grue answered, ``Genesis can handle herself.  She can always make a new body with her powers.''



``And her \emph{real} body?  She had it sent to my \emph{lair}.''



Grue paused.  ``Your lair could be on fire.''



``Exactly.''



He considered for a few moments.  ``Alright.  Just let me call Bitch.''



``Don't.''  I stopped him as he got his phone in hand.



``What?''



``A call at the wrong time, her ringer going off, it could mean alerting the enemy about her position or distracting her.  Wait.''



He nodded, and we ran.



Grue was letting his darkness dissipate, for the most part, as we were under cover and out of the way.  We made our way to the storm drain, using the wall for support.  We headed through the secured doors and into my cellar, then up the stairs to the main floor.



My lair wasn't burning down, but I could see the faint flicker of flame on nearby buildings through the slits on the shutters.  A quick investigation with my power showed that it wasn't anything serious.  I set bugs in place as an early warning system.



We headed straight for the bedrooms.  I wasn't expecting to see what I did.



There must have been fifteen of them.  Kids, none of them older than ten, some as young as four.  There were three to a bunk, sitting up or lying down.  Charlotte was with them, the eldest.



``Don't be mad,'' she said, in a small voice.



``Mad?''



She spoke quietly, as if the kids wouldn't hear, ``I didn't know where else to take them.  Sierra said we had to hide, that Mannequin was coming.  I saw him killing people without even moving.  He went after families, but he was focused on the parents, not the kids.  He killed them and let the kids run--''



``Stop.''  My voice was harder than I meant it to be.  ``I don't want to hear it.''



\emph{This is my failure}.



``I didn't know where else to take them.''



``You did good,'' I said.  I sounded like Burnscar did.  No emotion behind the words.  ``Someone else should have come here.  A girl or a woman, probably with an escort.''



Charlotte didn't answer, but moved aside.



\emph{Genesis}.



Genesis slept on one of the bunks I'd set aside for my employees.  Her face was contorted in an expression of concern.  Average looks, if a little round-faced, she had long eyelashes, and her auburn hair was a mop.



She had to sleep to use her power.  Could we afford to disturb her?  If we tried to move her and she woke up, would it mean taking her out of the middle of a fight where she could do something to Burnscar or Mannequin?



``Where are the rest of my people?'' I asked.



``Sierra divided us into teams and sent each of us in a different direction, telling us to get people to evacuate.  I almost ran right into Mannequin.  I hid and saw him attack.''



I felt out with my power, sticking exclusively to the building interiors, to avoid inadvertently barbecuing my bugs and frittering away my resources.  I used the bugs in the area to try to get a headcount.  The geography and the spread of people in this area was becoming familiar to me.  Very few were still alive and in this area.  Too many had died.  How many bodies were there?  Thirty?  Forty?



I didn't want to think about it.



``Charlotte, did you come in through the front door or the other entrance?''  I asked.



``Front door.  I was thinking about taking these kids and running for it, but I didn't know if you'd want--''



``Secrecy is not that important right now.  Take them down to the storm drain and stay there.  It's more or less fireproof, it's not going to collapse on their heads, and it's a better hiding spot than this.''



It seemed like getting orders invigorated her.  ``Okay.  Come on, guys.  Get ready, shoes on, this way.''



The kids began to get sorted and follow Charlotte's instructions as she herded them out of the room, staying by the door to ensure nobody was left behind.  There were no complaints and there was nothing like chatter or crying from the kids.  How many of them had watched their parents die for them?  They were so stoic, or shocked.



Grue looked at me, ``What are you thinking?''



``They take cover, we stay.  I'm going to try to use my swarm to get a sense of where Genesis is and how the fight's going.  The second things go south or this area gets too dangerous, we get her out of here.''



``You'll need this,'' Charlotte said.



I hadn't noticed it with all the people in the room.  At the foot of the bunk, in the corner of the room, there was a folded up wheelchair.



\emph{Can't ever be easy}.



``That might complicate things if we have to run for it,'' Grue said.



I didn't have a response to that.



Charlotte left with the kids, and we took the time to manage our wounds.  I headed into the ground floor bathroom to run cold water over the burns on my legs and back.  Grue sat on the toilet's lid and began gathering the necessary things from the first aid kit.



My power found Genesis, but only briefly.  She was big, some sort of flying pufferfish with a hard exterior and tentacles.  It was a hard image to piece together.  She floated slowly over the streets, and the bugs that I had on her died as Burnscar pelted her.  I tried to send some bugs after her, but she disappeared into the side of a burning building as they approached.  I tried and failed to find where she'd teleported to.  Frustrating.  Whatever her destination, it was a place my bugs couldn't touch, so I had to wait for her to move away or start attacking from another vantage point.



Nearly half a year ago, I'd gotten my powers when I was trapped in a locker, wanting to be anywhere but where I was then.  I'd reached out, my mind extending out for something, \emph{anything} to distract me and draw my focus away.



I wasn't trapped in a locker, but I felt very close to how I had then.  Except it wasn't the feeling that I was trapped.  My power's range hadn't increased.  It felt like that in a different way.



``We can't do this,'' I said.



``Hmm?''  Grue had torn open his pants leg and was suturing one of the cuts.



``We can't endure this.  We won't last.''



``We got unlucky and took the brunt of it.  We'll get a breather.''



``Will we?  These guys are experts in preying on weakness!  They're going to target us and come after us until we can't defend ourselves, they'll kill us, then they'll go after Panacea, or Armsmaster, or Hookwolf, or Noelle, and they'll do the same thing!''



``Taylor.''



I pushed myself to a standing position.  ``They're going to do the same thing they're doing to us, and they're not just going to win.  They're going to ruin everything while they do it!''



``Stop!''



I hobbled past him, and he grabbed my wrist.  Between anger and the fact that my sleeve was wet with the water of the shower, I managed to rip my hand from his grip.  ``Don't.  Don't do that.''



``What do you think you're going to do?''



``I'm going out there.  They're just bullies.  They're powerful, they've got every advantage, but that's all the more reason we can't let them get away with this.  I'll bait them out, or find where they're hiding.  I can take Burnscar down if I can get the right bugs to bite her, or sting her enough times.  I just have to do \emph{something}.  I can't just stay here and let them get away with this.''



``You're so hurt you can barely walk.  If they find you, you won't be able to run.''



``Sick of running.''



He stood and followed me.  He got ahead of me despite the fact that he was probably hurt worse than I was.  I ducked around him, and he pushed me against a wall.  ``Don't do this.  If you want to get revenge on those guys, if you want to help your people, you need to stop, rest, recover and plan.''



I struggled briefly, but the pain in my ribs and the burn on my back made that far more trouble than it was worth, and it was already pretty futile.



Hated this.  Hated feeling weak, even if it was Grue I was comparing myself to.



My bugs alerted me to movement from Genesis.  I didn't say anything to Grue, and simply waited as she grabbed her wheelchair, unfolded it and transitioned into it, before wheeling out into the hallway.



``Did we wake you?'' Grue asked.



``No.  I can't be woken by anyone except myself if I'm like that.  It's more like a coma than sleep.  You were watching me?''



Grue and I nodded.  He must have felt self-conscious, because he backed off, letting go of me.  I did note that he positioned himself between me and the end of the hallway.  I wouldn't be able to run for the cellar or the front door without going past him.



It didn't really matter.  He was \emph{right}.  Maybe I would have gone on if he hadn't stopped me, using my anger and frustration to drive myself forward until I got myself killed.  Grue and Genesis had, in their individual ways, interrupted that.  I felt simultaneously angry at him and embarrassed that he'd had to stop me.



``What happened?'' I asked Genesis, trying not to look at Grue.



She glanced between the two of us.  ``Realized Mannequin was using a gas, got a form together to fight that and occupy him, like you recommended, but he wasn't there when I reformed.  Burnscar was.''



``Mannequin forfeited his turn.  Burnscar went up next,'' I explained.



``Ah.''



``You manage to stop her?''  Grue asked.



``No.  I wasn't prepared to fight her, but she couldn't really hurt me either.  She left.''



``Can you get a body together to fight the fires?'' I asked, hugging my arms against my chest.



``I'll try.  My reserves are low.''



``Thank you.''



``I'm sorry I wasn't able to stop them.''



Grue got his phone out while Genesis retreated back to her bunk.  I made my way upstairs to curl up in the armchair.



So many dead because I couldn't save them.  I felt doubly guilty because my reasons for regretting their deaths were partially selfish.  It was a deathblow to my plans to seize my territory, earning Coil's respect and make inroads into saving Dinah, one way or another.



I took off my mask and let it drop to the ground.  My costume, I saw, was in tatters where it had burned.



Our enemies were good, they were smart.  Mannequin had been toying with us, and we'd taken that advantage and beat him to the ground with it.  But every action was calculated.  Cherish was informing them, Shatterbird was apparently smart in other ways, and Jack was the brains of the operation.



Had Jack calculated things so everything would play out the way he wanted, like Mannequin was?



Grue appeared at the top of the stairs.  ``Bitch isn't replying.  We should go look for her.''



``Okay.''



``You okay?'' Grue asked.



``\emph{Pissed}.''



``Me too.  Though I get that you have more reason to be angry.''



``I just--'' I stopped, clenching my fists.  ``I don't--''



I blinked back tears.  \emph{Fucking contact lenses.}



He wrapped his arms around me in a hug.



My face was mashed against his shoulder, his grip was too tight, my back was sore where his hand touched a spot near the burn.  There was also that mess of awkwardness from when I'd confessed my feelings for him, that now seemed so minor and distant compared to everything that was going on.



``We'll get through this.''



``No,'' I said, pulling away,  ``Not like this, we won't.  We fight them every time they come, we're going to be worn out, exhausted from always being on our guard, and if these past fights have been any indication, we won't make it through eight rounds of this.''



``The way you phrase that, you don't sound like you did in the shower.''



I shook my head.  ``No.  Because I've realized Jack wants us to focus on each of his people, one by one, because he knows it's going to play out like it has so far, and that we won't make it through eight rounds of this.  Let's change that dynamic.  We take out testers before they get their turn.  We go on the offensive.''



``Offensive?  Dinah said that a direct attack would be suicide.''



``So we go for the indirect attack.  They want to play dirty?  Let's play dirty \emph{back}.''





