





Bentley had been turned on his back, and Sirius had one side of Bentley's ribs in his jaws, pulling. Bitch was holding the other side, tugging on it with her entire body in an effort to pull it apart.  Bastard was chained to a streetlight, lying on the ground with his chin on his front paws.  He had shrunk from the size he was before.



\emph{She's alive}.  After Bitch had gone incommunicado, I'd worried Burnscar had gotten ahold of her.



The flesh of the bulldog's monstrous form was decaying, sloughing off and putrefying into a liquid slop over the span of seconds.  As the tissues connecting the bones disintegrated, they became loose, bending in place.  Bitch was trying to get the ribcage apart before the remainder of the flesh collapsed in on the dog's real body.



``Found her,'' I spoke into my phone as I hurried towards her, my rain boots splashing.  ``Yeah.  Contact the others about meeting.''



The pain in my legs made me gasp if I stretched my foot out the wrong way, and each gasp only triggered the pain in my ribs.  The air was heated, though there were no fires in the immediate area.  The hot, smoke-filled air combined with the pain in my ribs to punish even my shallower breaths.



``The fuck are you doing here?''  Bitch asked.



I drew my knife and held it by the blade, extending the handle towards her.  ``Helping.''



She didn't respond, but she took the knife and climbed partway into Bentley's body to start cutting him out of the protective sac.  I stepped in and used my shoulder to help leverage the ribcage open.  My legs screamed with the strain, but I could deal with the pain.  It would be better to suffer some pain than let Bitch get crushed inside Bentley's chest cavity.



She climbed out with the bulldog draped over her arms, falling to her knees the second she was free.  She laid Bentley down on the ground.



``Is he okay?''



She checked.  ``He's breathing.''



``Good.''



Her eyes narrowed. ``Don't act like you care.''



``I \emph{do} care.''



``Fuck you.  You heard what that psycho whore said and now you think I like you.  I don't.''



``I'm not thinking anything along those lines.''



``You're probably already trying to figure out a way to use it against me.  Fucking hate people like you.  Manipulative, two faced--''



``Hey!'' I shouted, cutting her off.  Sirius growled at me.



Bitch brandished my own knife, pointing it at me.  ``Do you know how much fucking simpler my life gets if I get rid of you?''



``It doesn't.  You might get the Nine off your case for a few days, but you'd be facing every test after that all on your own.  Believe it or not, I'm \emph{on your side}.  I want to help you through this mess.''



``Don't bother.  Go, leave.''  The knife didn't waver.



``I'm not going anywhere unless you're coming with me.''



``Getting cocky because you think I can't cut you.  Don't forget that you can be \emph{chewed}.''



I gave Sirius a glance, making sure to keep my head still so I didn't give off any sign of hesitation or doubt.



``If you were going to hurt me, you would've done it while Burnscar was threatening you.''



``I don't like being told what to do, so no, I wouldn't have.''



\emph{I doubt that, }I thought.  \emph{You don't like being told what to do by a stranger, maybe, but I'd bet you could be happy if you had a stable environment and consistent leadership.  }``If you carry out their tests and join them, they'll be telling you what to do for the rest of your life.''



``I don't care about the test!'' she shouted.  I could see Sirius tense, ready to attack.  ``I just want to be left alone!''



``I know the feeling.''



``You don't know anything!''



``Screw that!''  I jabbed a finger in her direction.  ``Maybe my life hasn't sucked as much as yours did, but I've \emph{been there}!  I've been hounded every fucking day by people who only wanted to make me miserable!  Every day, getting so tense that I'd feel like throwing up in the shower before leaving for school, and I'd have headaches before noon!  I spent weeks hiding in the bathroom during lunch breaks because they wouldn't \emph{fucking} ease up on me!''



``Boo hoo.  I could tell you what \emph{I} put up with.''



I shook my head, and took a deep breath.  I forced myself to calm down before I spoke.  ``I'm not interested in a pissing contest, Rachel.''



``Because you'd lose.''  She poked the knife in my direction, as if to punctuate her statement.



``Because this isn't a competition, and yeah, I'd lose.  I'm trying to tell you that we're not that different.''



She scoffed.



God, my legs and feet hurt.  My ribs weren't exactly sunshine and rainbows either.  I felt like I had to do something to distract myself.  If it hadn't been my legs that hurt, I would have wanted to pace back and forth, or run, or something.  I tried to focus on Bitch.  ``Fine.  Don't believe me.  Here's the nitty-gritty facts, then.  You're a member of our team.  We need you, and whether you like it or not, you need us.''



She scowled.  ``I--''



``Don't say you don't.  Don't say you could manage on your own.  You've seen these guys, and you're \emph{not} stupid.''



She looked down at Bentley, putting one hand in front of his snout, as if to check he was still breathing.  ``All you're spewing out of your mouth-hole are words.  You only want to help yourself.''



I wished there was something I could have hit, something I could have thrown.  I settled for an enraged groan.  ``What's it going to take to convince you!?  Why can't you understand that I can and \emph{have} put myself in harm's way for you?  That despite all the shit between us and everything we've gone through, you're my \emph{friend?}''



``You are \emph{not} my friend,'' she didn't look up at me as she uttered the words.



``Fine!  I've accepted that.  But you're \emph{my}\emph{ }friend, even if I don't like you half the time.  You're my teammate.  We're \emph{similar.  }The only difference is that you went through your shit years ago, and I just got through dealing with mine a few weeks after I joined this team.  We've traveled down the same paths.  Whether you like it or not, we're \emph{kindred spirits}.  We both struggle with the social--''  I trailed off.



Bitch had reacted to something I'd said towards the end there, flinched, almost.



I sighed.  \emph{This isn't accomplishing anything}.  I looked at my territory.  The plumes of smoke had turned the sky a gray-black in color, some of which glowed faintly orange with the reflected light of the fires.  The occasional spark floated through the air from one of the fires that burned around a nearby corner.



She broke the lingering silence, ``Coil told me that people would leave me alone if I got powerful enough.  If I had allies, if I had money, if I scared my enemies enough.''



``When was this?''



``Before I joined the Undersiders.  He didn't tell me who he was.  Left me a phone with some cash, then called me a while later.  Fucking words that sounded good.  Learned my lesson.''



She'd spent years on her own, on the streets with only the company of her dogs, running any time a cop or cape came after her.  I itched to ask her if she'd suddenly had an increase in the amount of trouble she faced before she came to Brockton Bay.  Trouble that could be precipitated by a certain ambitious supervillain?



No, it wasn't the time.



``You know that joining the Nine would get you the opposite of that.  It wouldn't be the kind of power that gets you left alone.  It would be a life of being constantly chased, always in the company of people who are ten times as manipulative and two-faced as you \emph{think} I am.''



``I \emph{know},'' she spat.



She picked up Bentley, then adjusted her grip to touch his nose with one hand.



Whatever.  Down to brass tacks.  I gave her a second to cool down, then spoke, ``They killed your dog, hurt Bentley, killed my people and torched my territory.  I want to take these fuckers down, no holds barred, and we're going to need your help if we want to pull it off.  Screw going on the defensive, I--''



``You had me at no holds barred,'' she growled, rising from her crouch.



I didn't dare to open my mouth, not with the risk of angering her and changing her mind.  I nodded instead.



Together, we limped back to my lair.  Every step I took was a chore.  Where Grue and I had supported each other, Bitch didn't offer me anything.  It bothered me a little; we could have ridden Sirius if we'd cooperated to help each other onto his back, but that wasn't apparently in the cards.



My bugs found Genesis a few blocks away.  Or, rather, they found something that approximated a blend between a slug and a rabbit.  My bugs identified two bulbous eyes, two tentacles or floppy ears and a body that hugged the ground.  The insects I had resting on the surface of the water could feel it flowing up and to the sides of the slug.  A small mouth jetted streams of it at the fires of a building near her.  I \emph{assumed} it was Genesis.  Educated guess.



One of these days, I was going to run up against something strange and assume it was her, only to be unpleasantly surprised.



I drew words and symbols with the bugs.  Shortly after, the flow of the water stopped and the consistency of her body began to break down.  She was on her way back.



Charlotte had taken the kids away, so my lair was empty as we made our way inside.  Bitch assessed the area and then headed into the bathroom, going for the first aid kit.



``Want help?''



She glared at me.  Answer enough.



I headed upstairs and stripped my mannequin of the costume I'd largely completed.  Then I removed my rain boots and began the torturous process of peeling out of the costume I was wearing.  I'd put off investigating the damage in favor of finding Bitch sooner.



Removing my mask wasn't a problem, but unstrapping my armor and getting my arms out of the sleeves made my ribs ache.  A fresh bruise had layered on top of the old one, black and purple over a purple-green.  I had to pause for a minute to catch my breath before I began on the legs.



I'd been wearing waterproof tights under my costume, and I cringed to think of the fact that I'd been wading in filthy water with the injuries exposed.  I got the first aid kit I'd brought down from my room and found a pair of tweezers.  Tatters of melted plastic from the leggings clung to the creases and edges of the burn.  Slowly, carefully, I worked my way down, removing the black fragments, digging in where necessary.  Every area I cleaned, I disinfected.  The largest burn covered my right heel, the top of my foot, and half of my calf, but the toes were okay.  The other marked the left ankle, heel and a patch small enough to cover with my hand on the shin.  There was less damage, but there was more melted spandex crusting it.  If I had second degree burns, it would be there.



The disinfectant virtually hissed as it touched my burns.  I applied it liberally, then got out the gauze and antibiotic cream.



It hurt as much as the lingering effects of Bakuda's pain grenade, but there was also the knowledge that it would take forever to heal.  I wouldn't be able to wear skin-tight leggings over the injured area.



\emph{Bastards.  }This pain was nothing compared to what they'd subjected my people to.  How many people had lost parents, loved ones, friends?  Homes?  I couldn't even complain to myself about the burn without feeling guilty.



Genesis was the first one to arrive upstairs, carried by one of her remotely controlled images, a crude rendering of a man who draped her in a chair and then faded as she woke.



``I couldn't put out any of the major fires,'' she said.  For someone who had just spent four fifths of the day sleeping, she looked exhausted.



``Thank you for trying.''  I took the wire cutters to the inside of my burned costume's leggings.  Each squeeze got me only half an inch of cut material.



``What next?''



``I've outlined a basic plan with Grue.  He contacted the others.  They should be arriving shortly, and we'll all discuss it together.  Tattletale doesn't think Burnscar's going to come back anytime soon, but I've laid out spider-silk tripwires over the area, just in case.''



``A plan?''



``Of attack.  It's easier if we wait until everyone's arrived before I get into it, so I'm not repeating it too many times.  Might even be smarter, if Cherish is looking in and trying to read my emotions to figure out what we're doing.''



``\emph{Attack}?''



``Being careful and being on the defensive isn't getting us anywhere.''



``It's keeping us alive.''



I shook out my costume and examined it.  Progress was too slow.  I put down the wire cutters and got the plastic lighter from my utility compartment.  I proceeded to burn through the material on the inside of the leggings, from the cut I'd made all the way to the crotch, then back down the other side, putting out any flame that lingered.  I was nearly done when I finally responded,  ``I don't think it is.  We're still dying.  It's just\ldots slower.  Can you honestly tell me we're going to survive another two confrontations like this?''



``So you want to be aggressive instead?  Suffer a fast death?''



``Yes to the first part, no to the second.  Look, they're good because they're \emph{experienced}.  Jack has been doing this for years.  He knows the exact balance he needs to strike, to be unpredictable enough that we can't plan against them, but clever enough that we can't catch them off guard.''



``But you want to try.  To catch them off guard, I mean.''



``Yeah.''



``It's suicide.  Like, what are the odds you're going to make it through a third round?  If we have a fifty-fifty chance of dying in a given confrontation, that's, what, a one in eight chance?''



``You're better at math than I am.  Sure.  Except we're not going to fight them head on.  Tell me, what are the limits on your abilities?''



``There really aren't any.  If it makes sense, if it's self-sustaining, with organs and an energy supply, it's easier on me.  I don't need to take up as much of the load with personal effort.  Bigger and denser forms are more taxing, too.''



``What about materials?  What can you use to put a body together?''



``I\ldots don't know.  I can control it, sorta, but my power chooses for me.  I visualize it as I use my power, I drift off, and I go into that sort of twilight state when you're just barely almost asleep, and your mind wanders.  Anything I haven't firmly put together in my head gets filled in with the stray thoughts and imagination.  I never put too much effort into the material, unless I wanted something like armor or stone skin.''



\emph{So ridiculously powerful}.  If I had her power\ldots damn it.



``And special abilities?  You can give them to your forms?''



``I have to visualize the mechanism, the organs or whatever that make it work.  I only have a limited time before I'm knocked out, so time I spend on that is time I'm not working on other stuff.  Like the form I was just using, you didn't see it, but--''



``I saw it.''



``Right.  The bugs, right.  Well, I visualized the water suction system and the water gun, but because I didn't focus on the body, it didn't have arms or legs, and it was slow, and because it didn't have vital organs, it drained me.''



``Okay.''  I held up my costume with the legs and feet reduced to tatters.  I turned my attention to a box behind my chair, tucked beneath a shelf of terrariums.  A small tide of roaches lifted it and carted it to me.  Inside were the scraps of fabric and mask left behind after Mannequin's first retreat.  I hadn't wanted to spare any material.



``Why are you asking?''



``Trying to assess the resources we have at our disposal.''



I heard a car door slam outside.  That would be either Grue or a collection of the others.



Genesis used her hands to shift her position in her seat.  I glanced at her legs.  They were thin.  Atrophy.  She'd been in a wheelchair for a while.  When I looked up, I saw she'd caught me looking.



``If you have a question, I'd rather you ask than keep wondering.''



I felt my face heat up, and quickly turned my attention to the fabric of my old costume.  I used the roaches to arrange a patchwork on the floor, using the tattered scraps.  My spiders crawled from the terrariums to begin connecting the pieces.  It didn't have to be pretty.



``Really.  Ask.''



``Were you disabled because of your power?  A side effect, or something that happened in costume?''



She shook her head.  ``I've been in a chair since I was four.  No, if anything, it's the other way around.''



Other way around?  My first thought was trigger event.  The second was, \emph{maybe that idea about people being stronger if they get their powers at a younger age is true after all}.



As I mentally categorized my musings, I felt them connect with a bunch of other thoughts.  Of the six Travelers, three were among the more powerful capes in Brockton Bay that I'd met.  In terms of sheer destructive effect, Sundancer and Ballistic were top-notch.  Genesis was top of the line in sheer utility and versatility, a combatant that could endlessly return to the battlefield with whatever form she wanted, provided that her real body was left unmolested.  Topping it off, Noelle was apparently so powerful she had to be kept in quarantine.  Trickster was impressive, if not quite in the same class as his teammates, and I had no idea what Oliver was all about, since he didn't have powers, as far as I knew.



How had they come together?  If I ran with the theory that Genesis somehow had her trigger event at four and was more powerful as a result, did that mean the other powerful members of the group had done something similar?  If so, how were they connected?



Or was I thinking along the wrong lines?



My bugs counted the people who'd exited the car and were heading through the storm drain.  A group.



``The others are coming in.  Your team and Regent.''



She smiled a little, but it was almost a sad expression.  Resigned.



Back when I'd first talked with Sundancer, I could remember asking her about her experience with the Travelers.  What was it she'd said?  Intense, violent, lonely.  Lonely despite the fact that they were constantly in each other's company.  I couldn't exactly remember what Sundancer's explanation for that loneliness had been.  It had been vague, hadn't it?



Seeing Genesis's expression, I suspected Sundancer wasn't the only one who felt that way.



The others made their way upstairs, followed by Bitch.  They gathered around my room, all standing.  I moved to stand, myself, but Trickster gestured for me to stay seated.



``You okay?'' Regent asked.



``Alive.  Hurts like hell.''



Through my swarm-sense, I felt a truck park outside.  Grue let himself in through the front door.



Before long, all were present.  Grue dialed Tattletale and put the phone on speaker.



``Yo,'' her voice came through.  ``Me and Coil here.''



``Skitter wants to attack the Nine, remove a tester before they get their turn.''



Trickster whistled.  ``Risky.''



``Look at it this way,'' I said.  ``Um.  How many police forces and superteams have tried to beat the Nine?  How many divisions of the Protectorate or alliances of cape teams have tried to beat them?''



``Lots,'' Trickster said.



``Too many to count.  The Nine play things like my team does on good days.  They pick their fights, avoiding confrontations or disappearing when they aren't certain they can win.  When they do fight, they hit where it hurts.  \emph{We} do that.  Look at what Regent did to Shadow Stalker, what I did to Lung on both occasions.  And they terrorize their victims.  We do the same thing, unintentionally or not.  Grue is scary with the darkness, Bitch's dogs make people shit themselves.  Me?  Everyone's at least a \emph{little} creeped out by bugs.  Tattletale and Regent are unnerving in a whole different way.  The Nine are \emph{us} on steroids.''



``That's not a very flattering comparison.''  Grue folded his arms.



``No.  But I think it's on target, and I don't think it's a total coincidence that they wound up considering \emph{two} members of our group for the Nine, Cherish's motivations aside.  So let's avoid playing things like Jack wants us to, let's not do things the way better heroes have tried and failed.  We play this like \emph{they} play this.  Unpredictable, calculated recklessness, we don't get caught up in a fight, and we think through every part of the plan.''



Grue shook his head a little, as if in response to some thought that crossed his mind.



``You will have my assistance,'' Coil said, ``Jack Slash needs to die, and you'll have access to all of my resources should you move forward.''



``Alright.  Thanks.  Bitch is on board, I think?''



Bitch nodded.



``Everyone needs to be willing to do this if we're going to move forward.  I'm not just talking about attacking these guys.  Sundancer, Ballistic, you guys have been holding back for a long time.  I know it's asking a hell of a lot, but\ldots are you guys prepared to kill?''



Silence hung in the air for a few long seconds.



``Yeah,'' Ballistic said.  ``If it's monsters like that?  I think I could.''



Sundancer hesitated.  She hugged her arms against her body, lips pursed.



``Mars,'' Trickster said, his voice quiet, ``You've killed before.''



``Accidentally.''



I thought back to her hesitation to use her power, back when we'd fought Oni Lee and Lung together.



``These guys aren't bystanders, they're not people,'' Ballistic said.  ``They don't even resemble people.  They're freaks, monsters.  The worst this planet has to offer.''



``It's not that simple.''



``By killing them, you're saving dozens, even \emph{hundreds} of people,'' I said.



``It's not that simple!''



``It really is,'' I replied.  ``I don't think we need an answer now, but you need to let us know before we begin.''



``What else do you need?'' Lisa asked, through the phone.



``We can't do anything until you find them.  I know the local technology is down, but--''



``But the local police and capes brought in emergency communications, just like Coil did for us.  I've been listening in on the radio transmissions.  Narrowing it down.  I could pull an all-nighter, listen in, and figure it out.''



``That's as good an excuse as any,'' Grue said.  ``If I'm going to help with this, I need to know that you're on the ball.  I don't do this unless everyone that's going to be on the battlefield gets six hours of sleep before we begin.  By that time, Tattletale will have a location.''  He faced me square on as he said it.



``I don't have normal sleep patterns,'' Genesis replied, ``In fact, I need to be awake to recharge.''



``Exceptions allowed, of course,'' Grue said, without turning away from me.



Six hours of sleep, with everything I had on my conscience?



``Sure,'' I lied.  ``But we attack first thing in the morning, or as soon as Tattletale pins them down.''



``First chance,'' he agreed.



``Is there any possibility that we could deploy Noelle?''  I asked Trickster.



``No,'' Trickster said.



``If she's as powerful as you say--''



``If Noelle used her power in this battle you're talking about, \emph{everyone} loses.''



The Travelers were way, way too fond of that line.



``Then, Coil, what kind of munitions do you have?''



``Most.  I can provide virtually anything, given time, but for tomorrow morning?  Well, tell me what you need.''



``I'm thinking explosives.  How much can you provide?''



``Hold on,'' Lisa cut in.  ``You're talking about Ballistic and Sundancer using their powers without limits, you want to use Noelle, now explosives?''



``And I'm talking about me using black widows, brown recluses and every nasty bug I have at my disposal.  I'm talking about us packing guns and grenades.  \emph{All} of us.  No holds barred.''



Trickster rubbed his chin.  ``Okay.  They broke the unspoken rules between capes, so there's no reason to actually follow those rules.  Sure.  But do you actually have a \emph{plan}?''



``Yes,'' I replied.  ``Keep in mind that this could change pretty dramatically depending on where we find them and what they're up to when we run into them.''



There were some nods from the others around the room.  My bugs had finished connecting the tattered pieces of fabric.  It wasn't pretty, but a few tugs to test it showed it was as sturdy as anything I'd made.  I draped it over my lap.  Until my legs healed, I'd be wearing my new costume for my upper body, with the tattered cloth as a skirt to protect my burned legs.



Then I told them what we'd be trying to do.





