





``We set up and act the second they stop moving,'' Grue's voice sounded through the walkie-talkie.  ``Be ready to move the instant Cherish alerts them.  We maintain unbroken line of sight over the Nine and between our squads.  Notify us and change position if you lose sight of 'em.  Everyone knows what they're doing?''



Various assents could be heard through the walkie-talkies.



``Maybe I should ask if anyone's unsure about what they're doing?'' he asked.



There was no response.



``Good.  Hold positions.''



The strategy was mine, but Grue was more comfortable than I was as a battlefield commander.  I was okay with him taking charge here.  Preferred it.



I raised my binoculars.  Seven members of the Nine were strolling down the street.  Jack, Bonesaw and Siberian were at the head of the group, and Jack was using his knife to try to cut down anyone he saw who didn't get under cover fast enough.  It was almost an idle amusement, rather than some mission or task he'd undertaken.  Most escaped, and he didn't go to any particular effort to chase them down, as though he were conserving his strength.



Cherish, Mannequin and Shatterbird were in the middle of the group, Crawler behind them, trailing behind with languid, casually effective movements that resembled those of a cat.  At the very back of the group, trailing even behind Crawler, was a hulk of a man who I took to be Hatchet Face.  He looked like he was rotting alive, and there were grafts of flesh and mechanical replacement parts filling in the gaps.



The majority of my attention was on Cherish.  Through the lenses of the binoculars, I focused on her face.  I watched the movements of her eyes, her facial expressions, and the tension in her hands.  Nothing she'd done thus far had indicated she was aware of us. Her attention seemed more focused on the handful people Jack had cut down.  As they walked, she looked down at each of the wounded and dying with the detached interest one might have for a car accident by the side of the highway.  She hadn't opened her mouth since we'd caught up with their group.



I \emph{so} wanted to jump in and save those people.  But it would be suicide.  Our priority was stopping the Nine.



Part one of the plan was simple.  Up until the point we engaged, we stayed as far away as we could while maintaining a visual and some ability to act.  We knew Cherish's power was more effective as she was closer to her targets.  If there was any element of surprise to be had, we'd have it by striking from a distance.



I spared a glance at Mannequin, changing the focus of my binoculars to the man in white.  Again, he'd replaced his parts.  His form resembled what I'd seen the first time I'd encountered him.



I turned my attention back to Cherish.  Shatterbird was saying something to her, her lips moving in the rhythms of speech beneath the glass beak/visor that covered the upper half of her face.  She was using her hands to punctuate her words.  Cherish didn't respond.  From the length of Shatterbird's speech, I took it to be some kind of monologue or lecture.



``Hey,'' Sundancer said from beside me, ``Ten or so seconds until we lose them behind that building over there.''



A quick check confirmed she was right.  The direction their group was traveling would take them out of sight.  I picked up the walkie-talkie, ``Moving forward.  You guys have eyes on them?''



``Yeah,'' Grue reported.  That would be our second squad.



``Yep,'' Trickster said, from the third.



I was already sitting side-saddle on Bentley, with Bitch ahead of me.  My burned legs didn't afford me much grip with my calves, so we'd taken a loop of the chain that surrounded Bentley and wound it under and over my lap and around my waist to secure me in place, connecting it with a carabiner in case I needed to get off fast.  I put one arm around Bitch for further support, and scooted forward to make room for Sundancer.



``Go,'' Bitch hissed the words the second Sundancer was in position.  Bentley lunged forward, leaping to the next rooftop and landing with enough force that I wasn't sure I could have stayed seated if I'd been riding normally.



Bentley was more of a bruiser than the other two dogs, with his front half adding up to almost twice the mass of the rear.  It made him weaker at the long distance leaps than any of the dogs I'd ridden thus far, but his powerful upper body also made him a strong climber.  It also meant he had the raw strength to carry three of us and the pair of heavy metal boxes that we'd strapped to his sides.  Our progress wasn't fast, but we did make our way up the side of the next building, Bentley's claws digging into the windowsills as he slowly and methodically ascended.  From that building It was one more leap and a short climb to the roof of the tallest building in the area.  I released my deathgrip on the chains and got the binoculars and walkie-talkie out.



``In position on the Demesnes Soft Tower.  Location of the Nine?''



``Lord and Tillman,'' Trickster answered me.



I found the intersection.  Once I had the right general area, it wasn't hard to spot them.  Crawler was conspicuous.



``Found them,'' I informed the others.



Our setup put Grue, Ballistic and Sirius directly behind the Nine, along with the metal cases of supplies we'd strapped to Sirius' sides.  Trickster and Regent were mounted on Genesis, who had taken a form not unlike the dogs.  The trio were positioned to the Nine's left.  By contrast, my group, with Sundancer, Bitch and Bentley, were positioned to their right.



Each of us were a little over a thousand feet away from the Nine, three city blocks, give or take.  It meant my allies were out of range of my powers.  It was a drawback, but I hoped it would balance out.



``They're moving with purpose,'' Tattletale sounded over the walkie-talkie.  Trickster was sending her ongoing video with a camera and directional microphone.  ``I think they're heading to Dolltown.''



``Dolltown?''



``Parian's territory,'' Ballistic said.  ``She controls these giant stuffed animals.  Cordoned off an area in my district before I made my claim.  I haven't gotten around to dealing with her yet, with the Nine and all.''



``They're probably trying to bait the heroes out,'' Tattletale said, ``Killing in the streets, then attacking one of the safe territories that aren't controlled by us.''



``ETA for them getting to their destination?'' I asked.



``One minute,'' Tattletale spoke.



``Moving up,'' Grue reported.  ``You guys maintain visual.''



Jack was still attacking everyone he spotted.  How many lives would be lost in the meantime?  Worse, would Cherish notice our presence, or would Jack look for civilians and spot one of us on a rooftop blocks away?



Going into this with the element of surprise was almost too much to hope for.



I put my walkie-talkie down, but I kept my eyes on Cherish.  She hadn't spoken, and there was no change in her posture.



``Grue,'' Trickster said, ``Get in position fast.  I see the area where Parian marked off her territory.  If they're going to stop, they're going to stop here.''



I used the binoculars and found the area in question.  Yellow spray paint, rain coats and scarves had been used to form a line across a street.



Grue didn't respond, but that could easily be because he was focusing on riding.  Just in case, I asked, ``You have eyes on him, Trickster?''



``Yeah.  Grue and Ballistic are heading up to a spot where they can see everyone.  No danger.''



\emph{No danger}.  It was a loaded statement.  Burnscar wasn't here, but Tattletale was ninety percent certain that the pyrokinetic teleporter was off tracking down one of the `hero' candidates or Hookwolf to give them their tests.



My heart was hammering in my chest, and I knew that between one of these heartbeats and the next, one of the Nine could spot us.  If it was Jack or Shatterbird, we could be dead or bleeding out less than a second later.



``Set up,'' Grue ordered.



I unclipped the carabiner and hopped down.  Working alongside Bitch and Sundancer, I helped bring the boxes we'd strapped to Bentley's side to the edge of the rooftop.  We hurried back, Sundancer giving me a hand up.  I almost didn't feel the pain of my legs with the tension and adrenaline that thrummed through me.  Or maybe that was the industrial strength painkillers Coil had provided.



I didn't want to think about the fact that the drugs I'd taken might be the same ones that he'd used to drug Dinah.



A quick sweep verified that the area around `Dolltown' was largely empty of people.  The flooding was bad here, and only Parian's place was really on high enough ground to be free of it.  Just to make sure, I asked, ``Tattletale?  How many bystanders?''



``Going by the video feed?  Guessing there's between eight and twenty people in the buildings around you.''



``Then I'm set,'' I replied.  I strapped the `seatbelt' chain around my waist and hips and reconnected the carabiner.  Other voices echoed mine, confirming they were ready.



Halfway across the roof, Sundancer began forming her miniature sun.  I checked on the others with my binoculars.  Trickster and Regent were crouched at the corner of one building, and Genesis was dissolving.  Good.



Grue and Ballistic were arguing.  I was pretty sure.  I could see Grue grabbing Ballistic's shoulder with one hand and pointing at the Nine with the other.



``What's going on, Grue?'' I asked.



``He's chickening out.''



\emph{He's supposed to handle Cherish}.  I glanced at the Nine.  No sign of anything from her.  She was standing apart from the rest of the group, her arms folded.



``She looks like someone I used to know,'' Ballistic said, as if that was some kind of answer.



``Who?'' Trickster asked.



``Sadie.  From seventh grade.''



``Nope,'' Trickster replied.  ``Not in the slightest.  Your head's fucking with you.  Get the job done.''



``But--''



Trickster's voice was as hard as I'd ever heard it.  ``\emph{Now}.  Remember the deal we made.  Our promise to each other and to Noelle.  Don't fuck this up.''



Ballistic hesitated.  Through the scope of my binoculars, I could see him holding the foot-ball sized warhead in his hands.  ``She's a human being, someone with feelings, and tastes and--''



Regent was the one who cut him off this time, ``And she's someone that has forced parents to mutilate and kill their kids and she made them \emph{enjoy it}.  Then she left them to live with the aftermath.''



Regent sounded remarkably calm given the situation.



``She's my sister.  If anyone has a right to get sentimental, it's me, and I'm saying it's okay to off her,'' he finished.



``I--''  Ballistic broke off.



I shifted my attention to the Nine.  Jack, Siberian and Bonesaw were moving past the yellow lines.  And Cherish\ldots Cherish was turning to look in Grue and Ballistic's direction.  I could see her almost bounce in place as she got her feet under her and started sprinting, her mouth opening.



``Cover blown!'' I shouted into the walkie-talkie.  Taking my finger off the button, I called out,  ``Trickster, Sundancer!''



Sundancer sent her sun soaring around to the Nine, taking the long route so it could cut them off.  In that same moment, Trickster pointed a sniper rifle at a corpse on the street and swapped Cherish's position with it.



Part two of the plan, after finding them and getting into our positions, was to remove Cherish as fast as humanly possible.  If we accomplished nothing else, our goal was to do that and then make a run for it.  It would pave the way for future attacks and it would slow them down.



We'd left that task to Ballistic, with the idea that Trickster would take care of Jack.  Ballistic decided he didn't have it in him at the worst possible moment, forcing us to shift roles.



\emph{Damn him}.



Cherish was struck by Trickster's shot, blood spattering the pavement.  Her teammates left her behind.



``Don't have line of sight to Jack!'' Trickster reported.



``Hit the others,'' I told Sundancer.



``You mean kill them,'' her voice was quiet, her fists clenched at her sides.



``Kill them, then.''  I could see the sun growing as it flew.  It was maybe eighteen feet in diameter now.



``Just\ldots just tell me there aren't any civilians there, no bystanders.''



I looked through my binoculars.  The remainder of the Nine were making a break for it.  Mannequin and Siberian stood still, watching Grue and Ballistic, Crawler was barreling towards them, and Shatterbird had taken to the air.  Jack and Bonesaw were taking cover around a corner to stay out of Grue and Ballistic's line of fire.



The thing that had once been Hatchet Face scooped up the wounded and anyone he could catch and deposited them with his group.  Bonesaw had a scalpel out and was cutting the second the people were in her reach.  A throat slashed here, a stomach cavity opened there.  Intestines and muscle strung from one individual to another, connecting them together as their faces contorted in pain.  Some struggled to stand, to strike Bonesaw or push themselves away, but deft slices with the scalpel severed tendons and ligaments.  It was a kind of grim reversal, the adults utterly helpless and weak when faced with the child.



\emph{We'll never have another shot like this}.



``No,'' I said.  I even managed to sound convincing.  ``No civilians!  Go!''



``Then tell me where to move it,''  Sundancer's eyes were closed.  ``I can't see that far.''



``Out further, left, left, left,''  the miniature sun slid twenty or so feet with every order I gave as I tracked the enemy's position and the movements of the orb with the binoculars.  ``Short bit left and then out!''



I couldn't look directly at the thing, but I saw Mannequin and Siberian wheel around as the blinding light of the orb caught their attention.  Mannequin ran, and Siberian lunged forward.



The orb slid out into position around the mouth of the alley and then rolled over Jack, Bonesaw and Hatchet Face.



``Report!'' Tattetale's voice came from the walkie-talkie.  ``I don't have visual.''



``Sundancer just hit Jack, Hatchet Face and Bonesaw.''



``Where are the rest?''



``Crawler heading for Grue and Ballistic, Mannequin running down Tillman in Regent and Trickster's general direction.  Shatterbird's going for the bird's-eye view.  I don't think she's seen any of us except Grue and Ballistic.''



``Siberian?''



``Missing.''



``\emph{Shit}.  Assume they're all alive, then.  Sundancer's power still in that area?''



\emph{Alive?  }``It is.''



``Then keep it there!''



I glanced at Sundancer and she gave me a grim nod.



Crawler had reached Grue and was scaling the side of the building with surprising speed.  I'd taken him for a quadruped, but apparently his joints were modular.  His proportions were more simian, now, and he was climbing up the side of the building twice as fast as I could have run it if it were laid out horizontally.



Part three of the plan had been to hit them as hard as we could.  Trickster was using his rifle to take shots at Mannequin, but I couldn't see if it was having any effect.  Ballistic finally decided to contribute, and fired a warhead at Mannequin.  Then he reached into the box he and Grue had unloaded from Sirius's harness and grabbed two more.  He fired them into the smoke cloud that had expanded around Mannequin.



I could see Crawler reaching the edge of the roof, not twenty feet from Grue and Ballistic.



Part four of the plan?  Avoid direct confrontation.



``Trickster,'' Grue said, the one word buzzing over the walkie-talkies.



Crawler disappeared, and an empty pickup truck toppled from the edge of the roof to the ground.  Crawler was back in the vicinity of the other Nine, not far from Sundancer's burning orb.  Blocks away from Grue and Ballistic.



The monster lunged after Grue and Ballistic again, and was supported this time by Shatterbird, who conjured up a storm of glass shards to pelt the pair.  Ballistic retaliated by firing a warhead at Shatterbird, who prematurely detonated the explosive with a thick cluster of glass, shielding herself against the worst of the blast with another wall.  She drew more walls around herself and maintained her assault.



Bitch whistled, and Sirius started bounding across rooftops to head our way.  I could see Shatterbird turn and notice us.



That was fine.  I sent a payload of bugs her way; wasps and bees each carrying several spiders, and more expendable caterpillars and the like that were smeared in capsaicin.  I wanted to make absolutely sure she knew where we were and that she wouldn't ignore us.



Crawler reached the base of the building only to be switched with yet another car, resetting his position a second time.  He roared in frustration, then turned toward the miniature sun, breaking into an all out run as he charged for it.



``Sundancer, switch off!''  I called out.



The orb disappeared, and Crawler crashed through the alleyway, only barely avoiding Jack, Siberian and Bonesaw.  The edges of the alley were unrecognizable, and the walls were on fire, but the trio were untouched.  Siberian had Jack draped over one shoulder  and another hand clasping Bonesaw by the back of her shirt, holding her high.  The pavement was a molten liquid beneath them.



I clicked the button on the walkie-talkie and informed the others, ``Siberian's granting her invulnerability to Jack and Bonesaw!''



Tattletale said something, but I missed it over the roar of noise that came with Sundancer using her power.  She was forming another orb.  Everyone else was busy with their own things.



Siberian was protecting Jack and Bonesaw.  That was both good and bad.  We'd planned this strategy under the assumption that Siberian would come for us and we'd use the dogs, Grue's Darkness, my bug-decoys and Trickster's teleportation to keep our distance from her until we decided we needed to make a run for it.  All of that was in line with part four of the plan, maintaining our distance and avoiding a toe to toe fight.  In the meantime, we'd intended to use our ranged abilities to take out Jack, Cherish, Bonesaw and Burnscar.



She was protecting them, which we hadn't anticipated, but she couldn't do that \emph{and} come after us.



\emph{Or maybe she can}.  I saw Siberian virtually toss Bonesaw in the air, the girl wrapping her arms around the woman's neck as she landed.  Holding her two teammates, Siberian sprinted for Trickster and Regent.  She was fast, but it was a speed borne of her peculiar powers, more enhanced strength than augmented acceleration.  Not so different from Battery on that count.



Air resistance and inertia didn't hamper her in the same ways.  More than that, whatever it was that made her invincible and untouchable to any outside force, she had the ability to snap it out to affect any surface she touched.  Her strength was virtually limitless, and the pavement didn't shatter with her footfalls because she made it as untouchable as she was.



Shatterbird, meanwhile, was drawing closer, using the glass-storm to bar Ballistic's access to the crate of explosives.  Grue's power was serving to counter hers, and any glass that entered the darkness seemed to drop straight down like rain, bereft of her abilities.  Momentum still carried, however, and any glass shards that entered at a high enough velocity seemed to exit at roughly the same speed.



I wasn't sure about Ballistic, his costume was among the best money could buy, but I wasn't sure what that entailed.  Grue, at least, should be able to endure a beating.  Beneath his motorcycle leathers, he was wearing the costume I'd made for him and nearly finished.  It wouldn't protect his head, but his helmet would serve in a pinch.



Even if they wouldn't be cut to shreds, I wasn't sure they would survive if Shatterbird detonated that case of rocket launcher rounds with a shard in the right place or a large enough impact.



``Bitch,'' I spoke.  ``The boxes!''



Bitch was sliding off of Bentley's back, opening the first metal box and stretching out the contents.



The case was a piece of camping gear I'd noticed ages ago, when I'd first been buying things for my costume.  A watertight case for luggage with a metal frame inside that campers could stretch out to use as a drying rack for clothes and towels.



We didn't have luggage inside.  No, the box held parts of the mannequins I'd been using for costume design.  Strung together with silk, two mannequins dangled from the frame.



Bitch adjusted the way one mannequin hung and headed over to set up the other case.



My bugs had reached Shatterbird and started attacking her.  Brown recluses, capsaicin, wasps, hornets and bees.  I'd never attacked someone like this.  Not someone who couldn't heal.  I could see her thrashing, trying to stay aloft even as her concentration faltered.  The brown recluses were insurance of a sort.  If we happened to take out Bonesaw, it could mean Shatterbird was out of the equation as well.



The darkness Grue had generated around the rooftop disappeared all at once.  Grue and Ballistic crouched at the far corner.  Canceling the darkness was a signal.



The mannequins hanging from the first rack disappeared, replaced by the two boys.  Grue and Ballistic disentangled themselves from the metal frames and hurried to our side.



Trickster and Regent appeared soon after the other frame was up.  I could see Siberian on the rooftop.  They'd escaped just in time to avoid being caught in a melee with her.



Trickster rolled his shoulders, stretched his neck and adjusted his hat.



``Don't waste time,'' Grue growled.  ``Do it.''



``Times like this call for a certain flourish,'' Trickster said.  Trickster withdrew a small remote from his pocket and depressed the button.



The rooftops the other two teams had been situated on virtually shattered with the explosions.  The bazooka rounds had also carried a small collection of plastic explosives.  Since Trickster's team had only needed the sniper rifle, their case held a hell of a lot more.



Part five done.  Baiting the hook, reeling them in, then hitting them as hard as we could.



It wouldn't stop them, of course.  The only ones that explosion might have hurt were Shatterbird and maybe Mannequin, if he'd survived Ballistic's attack and slipped around through some other angle.  Ideal world, it would also slow down Siberian.  More realistically, I was hoping that they'd get pissed, and they'd get sloppy.



I chanced a quick look through the binoculars.  Crawler was stampeding towards the site of the explosion, Cherish was still prone on the ground, bleeding out from Trickster's sniper fire, and I couldn't make out the others.



Wait, no.  I could see rubble shifting as Siberian shrugged it aside.  It was enough debris that \emph{Crawler} would have been hampered, but even with her hands tied up in holding her teammates, she cast the chunks of concrete and brick aside with the same sort of ease that I might walk through a pile of balloons.  She shook her head, and her hair fanned out behind her, draping partially over Bonesaw, who was riding her piggy-back.



Jack wasn't folded over her shoulder anymore.  He was standing, holding her hand, a wide smile spread across his face.  He said something, some exclamation, without dropping his grin for a second.



And Shatterbird?  I looked through the rubble that had been cast over the street around the building.  She was lying on the ground, struggling to her feet.  The glints of glass shards sparkled for a hundred feet around her.  I quickly tossed my binoculars aside.  They'd be a liability if she attacked us, now.



Here was the gamble.  We'd hurt them, injured their pride, we'd maybe killed Mannequin and we'd incapacitated Cherish.  If Ballistic had been on the ball, he would have blown Cherish to smithereens.  As it was, a stray bullet wouldn't cut it.  Bonesaw's known talents included the ability to raise the dead.



Grue used his darkness to form a dozen false-images of shadow-shrouded silhouettes on nearby rooftops.  I did the same with my bugs, but mine were animated, moving.



We'd have to run pretty damn soon.  There were seven of us, but only two dogs.  It was less than ideal.  I'd tried to get Bitch to bring another dog, but she didn't feel any of the others were trained well enough to bear riders.



The remaining members of the Nine charged, Shatterbird rising from her position to fly straight for us, barriers of glass surrounding her.  Siberian carried Jack and Bonesaw with leaping bounds, while Crawler headed for us.



I crossed my fingers, watching intently.



Two ways this could go for the final phase of our plan.



Well, three ways.  But I was hoping the third possibility -my team getting caught and slaughtered- wouldn't happen.



The first way this could play out was that Shatterbird's flight over the buildings would make her faster than Crawler or Siberian, who had to climb or circumvent the obstacles.



When I'd brought this up during the meeting, assuming it would happen, it had been Tattletale who pointed out that I was maybe underestimating how fast Crawler and Siberian could be.  She was right.  Despite her ability to fly, Shatterbird was falling behind.



Which meant we went with plan B.



``You up for this, Grue?'' I asked, ``I could do it.  My plan, and I was first to volunteer.''



``No, you can't run fast enough with those burns.'' Grue replied, as he hurried to the side of the rooftop furthest from the Nine.  He glanced down. ``Trickster, I'm ready!''



``Just need an opportunity,'' Trickster said, watching the incoming members of the Slaughterhouse Nine.  They were closing a little too fast for comfort.  Sirius had arrived, and we were all getting saddled.  Bitch, Sundancer and I on Bentley, and Regent, Trickster and Ballistic on Sirius.  At Regent's orders, Sirius moved to Grue's side.



``Sooner than later!'' Grue said.



``Do you \emph{want} to die?'' Trickster asked.



``No, but I'm willing to break something!''



``Your call,'' Trickster said.  ``Three, two, one!''



Grue leaped from the edge of the roof.  In that same instant, Trickster swapped him with Shatterbird.



She tumbled for a second, got a grip with her flight, and then steadied.



Then Regent hit her with his power.  Shatterbird flew into the corner of the roof, was thrown off-balance and tipped into the gap between buildings.



And Grue?  I cast a glance backward.  He'd dropped out of the air where Shatterbird had been flying, landing on a rooftop a distance below.  I could see him struggling to his feet.



``Go, go!''  Trickster screamed the words.



Our mounts leaped down into the same gap where Shatterbird had fallen.  We made the usual zig-zagging descent down, leaping from wall to wall, and landed on either side of Shatterbird and Genesis.



Genesis looked like a cartoon caricature of a sumo wrestler, grotesquely obese and yellow skinned with eyes like black buttons.  She was hairless, unclothed and sexless, and her skin was translucent and oily.  Through the skin, I could make out the vague figure of Shatterbird, pounding on the walls of the stomach, her mouth opening in a scream that didn't reach us.  Glass shards were stirring around her, a blender whir cutting at the insides of Genesis's belly.



``She's going to cut through,'' I said.  ``Bitch, Regent, get the chains.  I'll try to stop her.''



Using my bugs, I formed words against the surface of Genesis's belly.  `Stop'.



Shatterbird only intensified her attempts.



I gathered some black widow spiders and pressed them gently against the shiny, translucent skin.  They were absorbed, drifting inside, and were soon crawling around the inside surface.  Genesis obliged me by opening her mouth, giving me a direct route for the bugs to travel.



``Hurry,'' Regent said.  He was winding the chain around the jello-like yellow hand.  Fingerless hands gripped the chain for further traction.



Shatterbird noticed the spiders.  Her eyes widened as the volume of deadly spiders trapped in the bubble with her increased.  I raked my finger beneath the message I'd drawn with the bugs, as if to underline it.  `Stop'.



She did.  Glass shards fell into a pool around her feet.



``Go!''  I shouted.



We ran, the two dogs side by side, pulling Genesis behind us like a chariot.



Drawing my bugs together, I covered us as best as I was able, creating other decoys, vague chariot-shaped lumps here and there, huddles of figures.



It would all be for nothing if they returned to Cherish, revived the girl and tracked us down.



``Left!'' I ordered.



Bitch steered left.  Regent hadn't heard, but as the tension on the chains pulled Sirius to one side, he caught on and turned as well.



My bugs served as a navigation system, feeling out the shapes of our surroundings so I could work out a suitable path.  We charged onward, with me giving occasional directions, until we found Cherish lying on the ground in a pool of blood.



``Get her!''



Bitch rode just to Cherish's left, Regent rode just to the right, and Genesis rolled right over the girl.  Cherish caught like glue, suffered an unfortunate few seconds of being dragged over the road's surface, and was then drawn into Genesis' bubble of a body.



My bugs gave me a sense of the Nine's locations, and my decoys gave them pause once or twice.  We could track them more easily than they could do the reverse, and we were soon far enough away that I couldn't sense them.



\sectionbreak



We only slowed when we got to Coil's underground base.  We parked the dogs and then headed for the series of barred and locked doors.  I glanced at Shatterbird and Cherish where they knelt in Genesis' rotund body.  We weren't really giving away information here. Crawler had apparently come this way, not so long ago.



It was a fifty-fifty chance whether Siberian and the other Nine would come this way.  Cherish wasn't around to give them information, but she might have provided details at an earlier point that Jack or one of the others could use to connect the dots.  We'd cross that bridge when we got to it.



Coil was there to greet us with a Tattletale and a contingent of armed soldiers.  We waited patiently as one of the soldiers scanned Shatterbird with a plastic wand.  He looked at Coil and shook his head.



``This way,'' Coil ordered.



\emph{How did he set this up so fast?}



Shatterbird's cell was large, twenty feet by twenty feet across, and the walls had the same textured black rubber soundproofing as the sound recording booths I'd seen in movies and on TV.  I couldn't see the speakers, but there was a noise similar to radio static filling the room, so loud I wouldn't be able to hear if someone spoke.



With our weapons trained on Shatterbird, we stood by while one of Coil's soldiers reached into Genesis's stomach and hauled her out.  She was chained to the ceiling with her arms stretched out to her sides, then divested of her costume, left only with a silk camisole and slip.  Coil's people wheeled in an x-ray machine and a tank of containment foam.



Shatterbird glared wordlessly at us until we'd exited the room and the heavy vault door blocked our view of her.



``She will be cavity searched and x-rayed to identify any hidden weapon or any devices Bonesaw or Mannequin might have implanted in her,'' Coil spoke, after the doors were closed and the white noise was blocked out.  ``Regent, we have a protective suit waiting for you.  In the event that she does acquire something she can use her powers on, or if she has concealed anything on her person that is small enough to avoid radiographic detection, the suit will shield you until you've finished.''



Regent nodded.



``She was bitten by brown recluses,'' I said.  ``I'd give her a full physical examination every thirty minutes, to be safe.''



``I'm afraid I don't know standard treatment for bites of that kind,'' Coil said.



Brooks stepped out of the crowd of nearby soldiers.  ``Sir?''



``Brooks.''



``I'm familiar with the treatment for the more dangerous spider bites,'' he looked at me, ``It's a protein-based venom?''



\emph{So the jerk is useful sometimes}.  I hadn't liked Brooks since Lisa had introduced me to him, but I could respect someone who knew his job.  ``Yeah.''



``Seems I can leave it to you, then,'' Coil said.  Brooks nodded.  Coil added, ``Failing everything else, it might serve as incentive to cooperate.''



``Or cause to get desperate,'' Tattletale said.  ``She might do something stupid if she thinks she'll die or suffer lifelong effects if she doesn't get back to Bonesaw.''



``Let's not give her the opportunity.  Regent, how fast can you seize control?''



``A few hours.''



``Start now.''



Regent headed off to get changed.



``That leaves our unexpected guest,'' Coil said.  ``Cherish.''



Regent hadn't yet escaped earshot.  He turned back to us.  ``She'll have a trap on her.  Small explosive looped around her neck with a lock and a deadman's switch.''



``Thank you,'' Coil said.  ``Tattletale?  See to it at the first opportunity.''



``Not a problem.''



We approached Cherish and Genesis. Cherish knelt in the small pile of glass shards that sat at the very bottom of the bubble.  Her hands were pressed against the inside of the stomach, causing it to bulge like a small child in a womb.  She was awake, but bleeding severely.



Coil gave the order, ``If anyone acts out of character, take them out of action as swiftly as possible and shoot the girl.''



There were nods all around.



Cherish's mouth moved, but the sound didn't reach us.



``I did not expect her, and I did not take measures for containing her,'' Coil said.  ``Keeping her on the premises may prove exceptionally dangerous.''



``The alternative being?'' Trickster asked.  ``Letting her go?''



``In the euphemistic sense.  Her value as a captive is minimal and we have no way to secure her until Regent can finish using his ability on her.''



``He's resistant to her power,'' Tattletale said, ``But that goes both ways.  Don't know how well he'd be able to control her.  She might break free.  Benefits of being family, I guess.''



``Then I would suggest, as Trickster said earlier, `letting her go'.  We execute her and remove her from the equation,''  Coil stated.



I looked at Cherish, and her eyes narrowed.  She knew \emph{exactly} what we were saying.  Killing someone in cold blood?  A little different than killing someone on the battlefield.



``Not giving you the go ahead,'' I said.  ``But I'm not about to stop you.  I'm washing my hands of this.''



``The intent was to remove individuals from the Nine before they could conduct their round of tests, yes?  This seems to be the most expedient route.''



``Not disagreeing,'' I said.  ``But I didn't sign up to be an executioner.  I manage my district and I help defend your city from outsiders, right?''



``Quite right.  No, I think your service this morning has been \emph{exemplary}.''



I only barely managed to avoid bringing up the deal about Dinah.  No, it was premature, the wrong people were listening, and I was worried he would point out the fact that my territory had been torched by Burnscar.



Best to keep quiet for now.  Rebuild, re-establish myself as leader of my territory, \emph{then} raise the topic.



Whatever happened, I needed his respect.



We turned our attention to our captive.  She had raised her hands above her head in a surrender position, despite the hole in her shoulder.



``Do we risk it?'' Trickster asked.  ``Letting her out?''



``Nothing she can't do outside the bubble that she couldn't do inside,'' Tattletale replied.  Coil nodded, and that seemed to be signal enough.



Genesis began to dissolve, and in moments, Cherish spilled out, wincing as she cut her hands and knees on the glass that Shatterbird had detached from her costume and weaponized.



Tattletale bent down and looked at the device that hung around Cherish's neck.  ``Small explosive, combination lock.  A bit paranoid?''



``No such thing as too paranoid,'' Cherish said, glaring.  ``Between my brother and the crap that Bonesaw and the rest of the team want to subject me to, knowing I'll die if I leave that thing alone long enough actually \emph{helps} me sleep at night.''



``Can't have that,'' Tattletale said.  Changing the topic, she asked, ``You like computers?''



``Computers?'' Cherish startled.  She seemed to intuit what Tattletale was doing.  ``Not saying.''



``Clever girl, but even that's enough of a clue.  Let's see\ldots four, five, four five.''  Tattletale tugged on the lock.  ``Nope.  Three, seven, three, seven.''



The lock popped open.  Cherish's eyes opened wide.



``There goes your bargaining chip.''



``I've got more,'' Cherish said, her chin rising a fraction.



``Do tell,'' Coil said, dryly.



``Certain teammate of yours paid me a visit.  Imp, I think her name was?  So hard to \emph{remember}.''



``What did you do to Imp?'' I asked.  \emph{Grue is going to freak out}.



Cherish smiled, ``She decided to help me get back at the Nine.  They're planning on inflicting a fate worse than death on me, you see.  There \emph{was} a reason I pretended not to notice you were all waiting in ambush.  Thought maybe the brat passed on word somehow, until you used that sucker-teleport on me and shot me.  Suppose you'll have to give me medical attention and keep me alive if you want the rest of the story.''



``And your other bargaining chip?'' Trickster asked.



``Grue.  I can sense him with my power.  I can also sense my team.  They got their hands on darkness boy.''



I swear my heart stuttered mid-beat.



Cherish smiled, but her glare didn't fade in intensity.  ``My teammates and I already talked on the subject of Jean Paul, aka Hijack, aka Alec, aka Regent\ldots  You got Shatter, and you got me.  We're compromised.  No way they're going to accept us back with open arms.  They'd kill us first.  So no, don't get your hopes up.  My teammates \emph{aren't} going to agree to a hostage exchange.''





