





``Where is he?'' I growled.



``As if I'm going to tell you.  To think Jack called you the clever worm.''



``Don't call me that.''  I felt a flare of irritation that bordered on anger.  Was that me, or was it her power at work?



Tattletale put a hand on my shoulder.  I shut my mouth.  She asked Cherish, ``What do you want in exchange for your help?  You want us to let you go?''



Cherish laughed a little, and it reminded me of Alec's own dry chuckle.  ``No.  Definitely not.  In exchange for the information about what the Imp is up to, you're going to give me medical treatment, you're going to keep me \emph{here}, and you're going to keep me \emph{safe}.''



``And for the info on Grue?''  Tattletale asked.



``I'm thinking a billion--''  Cherish winced as she moved mid-sentence and pulled at the wound.



``A billion dollars so you can scamper off to the other side of the world and live the good life while you hide from those bastards,'' Tattletale finished.



``Right.  Or are you going to tell me that's too much?  Is your teammate's life worth a smaller amount?  Where do you draw the line, Ms. Frowny-face?''



Tattletale glanced at me.  I looked, in turn, to Coil.  He gave me a barely perceptible shake of his head.  He wouldn't fork over the amount.



``You're not really in a position to be making demands,'' Trickster said.  ``You're bleeding to death, and we \emph{do} have the ability to hurry the process along.''



Cherish shrugged.  ``Bonesaw gave me the works.  Mesh sheaths for every major artery and organ, wire reinforcement for my skeleton.  It's not going to kill me anytime soon.''



I made a mental note of that.  Chances were good that Jack, Bonesaw and the other more vulnerable members of the Nine had some similar protection.  How differently would things have played out if Ballistic had used his power and blown them up?



``\emph{I }could,'' Trickster threatened.  ``Or we could wait and see which happens first: Either you agree to share the information we want or you slowly bleed out.''



``A game of chicken?  I'm down.''  Cherish prodded her injury with a fingertip.  It was clear it hurt, but she still stuck a finger into the hole and investigated some.  ``The auto-injection pump is dosing me with painkillers and antibiotics now.  First time feeling this stuff work.''



``Letting that\ldots lunatic perform surgery like that?'' Sundancer asked, shivering a little.  ``How?  Why?''



``Not much choice in the matter, but I was awake for the entire thing, and I read her emotions as she did it.  No hint of any traps or dirty tricks.''



Tattletale glanced at the bullet hole in Cherish's chest.  ``I'm suspicious it's so routine for her that there wouldn't even be a blip on the radar if she did try something.''



Cherish leaned forward, ``Are we going to do this?  Test your perceptive abilities against mine?  Some intellectual jousting?''



Tattletale shook her head.  ``She's stalling.  She knows time's on her side, because we need to rescue Grue sooner than later.  Longer we wait, the worse our position.''



``I admit I'm at something of a loss.'' Coil sounded pensive, as he looked at our captive.  ``Where do we put her?''



``Jack did research on you assholes,'' Cherish cut in, still trying to distract us, ``I know your schtick, Tattletale.  Pick at people's weaknesses, tell them stuff they don't want to know.  I can do the same thing.  I'm \emph{better} at it than you are.''



``It's a bit of a crazy idea,'' I said, ignoring her.  ``But what if we didn't stash her in this base?  Or any of the others?  We put her anywhere in the city, there's the risk that some unwitting John, Dick or Harry will come by, and she'll get them to help her somehow.  Can't station guards on her, so\ldots why not the water?''



``A boat?'' Ballistic asked.



``I could tell you a story,'' Cherish said, ``Little girl grows up with \emph{money}.  Daddy pulls in six figures, maybe seven.  Massive house, I expect.  Maybe horses, a mercedes, indoor and outdoor pools\ldots''



``I was thinking about a buoy,'' I replied, speaking over her.  ``Could even rig things so she's out of sight.  Cuff her to it, we can be pretty damn sure she won't be getting free.''



``But what about boats coming by?'' Sundancer asked.



``Almost no boats on the water,'' I replied.  ``Coastline is a mess, thanks to Leviathan.  Ships can't dock here.''



``Good,'' Coil said.  ``Then as soon as she is given some basic medical care, I'll have my men take her out there.  I'll need to work out measures to ensure she doesn't escape.''



``So the little girl who wanted for nothing still found a reason to run away from home.  Spent life homeless on the streets.  Stealing and dealing for petty cash so she could eat.  What would make someone leave home like that, Tattletale?''



Coil turned to the soldier next to him, ``Can you go find Pitter and bring him here?  I want her sedated sooner than later.''



The soldier nodded and headed off to find the medic.  He winked at Tattletale as he jogged by.  I'd met him.  Not one of Tattletale's soldiers, but I'd crossed paths with him.  Fish?  Seemed like he and Tattletale were getting along.



``That's a mistake,'' Cherish smiled.  ``Without my cooperation, you won't find them.  You won't be able to contact Imp or know where to look for her brother.''



``Tattletale?'' Coil spoke.



``You already informed us on most of that,'' Tattletale told Cherish.  She leaned against the wall.  ``Your method of communication with Imp.  You're planning on meeting her.  Afternoon?  Evening?''



``As if I'm--''



``Late afternoon. Thanks.''



``What?''  Cherish frowned.



``What time in the afternoon?  Four\ldots five\ldots six.  Six o'clock.  There we go.  Where?  Upper end of town or downtown?''



``I'm not saying anything!''



``You're telling me everything.''  \emph{Tattletale must be reading Cherish's tells.  Her body language, eye movements, her tone and word choice}.  ``Let's see, you're meeting Imp downtown around six.  You would have made it a place where you could talk with her for a minute while you were out of sight of the others.  Bathroom?''



Cherish didn't move a muscle.  Maybe she realized what Tattletale was doing.



``Bathroom, then.  Same building as the rest of the Nine?  Now we just need to dig up where they are, and you've got no cards left.  Unless you want to share that information in good faith.''



There was no response from our prisoner.



``Hmmm,'' Tattletale said.  ``She's cornered, and she's probably contemplating something like suicide by cop.  Or whatever the term is when the other group aren't cops.  She'd rather die than have us turn her over to her teammates, so she'll try a gambit like using her powers, knowing we'll probably gun her down.''



``Got any ideas?'' Trickster asked her.



``She liked the dead man's switch for her suicide collar.  Why don't we set up something similar?  Put a soldier on guard somewhere nearby.  We schedule it so he receives a note  from us every fifteen minutes.  If he doesn't get it, he passes a message to the Nine telling them exactly where to find Cherish?''



I could see Cherish tense.



``How do we get a message to them without them killing the messenger?''



``We can work it out.''  Tattletale shrugged.  She looked at Trickster, ``You think Oliver could handle it?''



Trickster nodded. ``I'll get him on thinking up some way to arrange this.''



``Tattletale.'' Coil spoke, ``Can you gather the rest of the details from her before we secure her offshore?''



``So long as she doesn't get stupid and try to do something more than talk.''



Cherish decided to speak up.  ``Who's next?  Who should I dish the dirt on?  Feeling homesick, Trickster?  Scared little boy pretending to be a leader.  It's your fault, you know.  She blames you.  Everyone does. They're even starting to hate you.''



``Can we talk without her in earshot?'' I asked.



Coil nodded and gestured for us to leave.  His soldiers moved to Cherish's side and gripped her arms.



``No point!''  Cherish grinned, ``I'll know what you're talking about.  Can't keep secrets from me!''



``But you won't be sidetracking us,'' I replied.



``You failed, you know,'' Cherish said, changing tacks.  ``When someone has an obsession like you do, it's like a giant neon sign to an empath like me.  All it takes is for me to peek into Coil's head, peek into the hearts of everyone else in this base, and I know you'll never get what you want.  You won't save her.  You can't.  Window of opportunity is long gone.''



I jabbed her where the bullet hole was.  The strength went out of her legs and she fell to her hands and knees.  I stepped back, drew in a slow breath and then kicked her in the face.  She fell to the ground.



``Skitter.'' Coil's word was without inflection.  There was no admonishment or warning to it.  I took it as a reminder of where I was, which might have been his intent.



``We can talk about that later,'' I told him, ``My priority right now is Grue.''



Coil nodded.



I glanced down at Cherish.  ``Hope Bonesaw reinforced your teeth while she was fixing you up.''



``She did,'' Cherish muttered, one hand to her mouth.



I kicked her in the head once more for good measure, and then turned away, my hands raised to assure the others I was done.



``That's enough,'' Coil said.  He signaled his men.  ``Take the prisoner to the coastline and find a spot to depart.''



Cherish was dragged off to a point further down the catwalk.  Her shouts reached us well after she was out of sight, ``Your boss is screwing you!  All of you!  You have no idea how badly!  You're cogs in his machine, and he's only steps away from pulling it all together.  Get rid of the Nine, stage the final play with everyone in their proper spots, but then he doesn't need you anymore!''



``Sowing dissension in the ranks,'' Coil said.  He sounded remarkably calm given what Cherish had been saying.  ``Nothing more.''



``Right.  She could be lying,'' Trickster ventured.



``She is.  Mostly,'' Tattletale said.



I doubted anyone believed what the three were saying.  At the same time, nobody here was in a position to walk away in response to this unconfirmed information.



``Tattletale, see to the interrogation,''  Coil ordered.



``Okay.''



``That leaves the remainder of us to decide on a way of rescuing the others.''



I fidgeted.  The idea of Brian in the hands of the Nine was\ldots daunting.  Was Siberian eating him alive, literally?  Was he at the mercies of Mannequin?  Jack could be torturing him for details on us.  Or he could be in Bonesaw's clutches.



Chances were good that they were pissed.  Jack excepted, maybe.  He'd seemed to \emph{like} our ambush.  In any event, any anger or sadistic tendencies were likely to be taken out on Brian.



\emph{Fuck}.  I kept imagining uglier and uglier possibilities.



``They're going to be waiting and ready.  We'll need help, I think,'' I said.



``Help?'' Trickster turned my way.  ``You're forgetting that the rest of the factions in the city have made a pact against us.''



``Not everybody there agreed,'' I said.  ``There was one group at the meeting that didn't agree to the pact.''



``Am I remembering wrong?''  Trickster asked.  ``Coil, Merchants, Chosen, Faultline's group\ldots''



``That's right,'' I said.



``What are you thinking, then?''  Sundancer asked.



``Coil,'' I said, ``You got some surveillance gear for Tattletale, right?  Can I see it?''



\sectionbreak



Trickster accompanied me.  We didn't get the benefit of Bitch's dogs.  She'd wanted to check on her territory and take care of her dogs.  I'd grudgingly agreed that she should take care of that, and Trickster and I had set off alone.



I gave him a sidelong glance as we ascended the stairs of the empty apartment building.  What had Cherish said?  \emph{Scared little boy}?  \emph{She blames you}.  \emph{They all do}.  I could remember Sundancer's remarks on the drama in the group and how lonely it was to be around them.  I recalled Genesis seeming less than thrilled when her team arrived last night.  Was Trickster at the center of it?  He was more ruthless than his comrades, which was interesting because his power was the least lethal.  It might have been a point of contention.  But what would he have done that the others would blame him for?



Could I comment on that?  Should I?



I remained silent.  We exited the stairwell at the fifth floor and entered a dark hallway.  I clicked on a flashlight, and we made our way down the hall.  Trash was piled everywhere, and I was all too aware of the maggots that were crawling on the floor, barely visible in the dim light.



``Which way?'' he asked.



I pointed.  A side benefit of my power was that it made it pretty damn easy to maintain my sense of direction.



We tried the doors for the two apartments that led in the right direction.  Both were locked.



Trickster touched the doorknob, then looked across the floor at the trash in the hallway.  The doorknob disappeared, and a chunk of wood fell to the ground.  He repeated the process with the internal mechanisms, and the lock was effectively transported away.  He opened the door and walked inside, going straight for the windows.



``Done this before?'' he asked.



I shook my head.  I was gathering my bugs, the stronger fliers, and drawing out lines of silk.  Trickster handed me the individual components.  A small spy camera, no larger than a tube of lipstick, and a similar microphone.  My bugs bound them together with silk and then stretched out more to distribute the lifting among the dragonflies, bumblebees and wasps.



``Okay, let's see,'' I muttered.



``\emph{Testing, testing, one, two, three\ldots}``\emph{  }My swarm managed some semblance of the words I wanted, a mix of buzzing, chirps and clicks to form the right pitch.  Some sounds were hard or impossible to make.  The `puh', `buh' and `muh' sounds didn't form, and I struggled to form something that sounded like a `t' in the middle of a word.  It was intelligible, but only barely.



It would have to do.



I ensured the rigging around the camera was more or less steady and then sent the swarm out the window.  I relied on my power to keep track of it while I opened the laptop Coil had provided and turned on the video feed.  When it had arrived outside the PHQ headquarters, I drew it together into a densely packed human form.



It took six and a half minutes for the Protectorate to react to the figure.  That bothered me, on a level.  Were they disorganized?  Or was it difficulty in communicating and marshaling their forces when they didn't have phones or other means of passing on alerts?  They gathered in the lobby.  I adjusted the camera the insects were carrying and made out Weld, Kid Win, Clockblocker, Miss Militia, Battery and Legend.  There were three more capes I didn't recognize.  Members of Legend's team?



Seeing them gave me pause.



As Miss Militia stepped outside, I pulled on the headphones, and Trickster did the same.



``Skitter?'' Miss Militia asked.



``\emph{Something like that},'' I replied using my swarm.  ``\emph{I wanted to talk.}``



``Given what happened the last time you were here, I'm not sure we're on speaking terms.''



``\emph{We have two of the Slaughterhouse Nine in custody.  We are prepared to turn one over into your custody.''}



``What?  I didn't hear that.''



Damn.  It sounded natural in my head, as I got them to make the noise, but I wasn't quite there yet.  Maybe it would have been better to just pass a phone to her.  I'd gone this route for the dramatic touch, and because I hadn't wanted them to trace us.



I rephrased, ``\emph{Shatterbird and Cherish have been captured.  We will deliver Cherish to you if you wish}\emph{.  We are done interrogating her}.''



``Interrogation.  You mean torture, don't you?'' Legend asked from where he stood in the doorway.



``\emph{No}.''



``Why?''  Miss Militia asked.  ``Why the offer?''



``\emph{You can put her in secure custody, and we need your help.}``



``For?''



``\emph{The Nine have captured Grue.  We mounted one successful attack this morning, we got two of theirs for one of ours.  They will be ready for a rescue attempt.  They know our powers.  Help us attack.  Help us catch them off guard a second time and stop them for good.}``



``You're not only asking us to fight the Nine, but you want us to fight alongside notorious villains.''



So I was notorious now?  Huh.  Couldn't let that distract me.  ``\emph{I'm offering you Cherish.}``



I could make out Miss Militia shaking her head.  ``I'll be blunt, Skitter.  I'm not Armsmaster.  I don't have a stake in personal glory or renown.  I'm not going to pussyfoot around, either.  Put a bullet in her skull and be done with it.  There's a kill order on them, nobody's going to charge you for murder.''



``\emph{Then work with us because it's the best way to stop the Nine}.''



``I refused Hookwolf when he made the same offer, and I'm going to refuse you.  The capes on my teams are good people.  I won't throw away their lives with a reckless attack.  We're going to develop our own strategies, plan, and find a safe way to target them.''



``\emph{And civilians die in the meantime}.''  I retorted.  \emph{Grue} dies in the meantime, if he wasn't dead already.



``We've tried the same strategies we use against Endbringers.  Multiple teams, allying with locals.  Sometimes we get one of them.  Sometimes we get three or four.  But we lose people, \emph{lots} of people, in the process.  The remaining members of their group always find some way of escaping. The fact that we tried and failed in going all-out gives them \emph{notoriety}.  They bounce back after an attack like that, and they bounce back \emph{hard, }with creeps, lunatics and killers flocking to them for the chance at that same sort of glory.''



``\emph{The difference between us and Hookwolf is that we've succeeded.  We have two of them in our custody.  You can't bide your time, organize, and wait for an opportune moment.  They have years of experience fighting people who do that.  Anything you try, they've probably dealt with.  We win by catching them off guard with powers they don't know about, powers they can't expect and interactions between powers.  Calculated recklessness.}``



``We can handle that on our own, with more calculation and less recklessness.''



``\emph{He's studied you.  For any member of your team with more than three months of experience, he already knows everything they can do, their tricks and individual talents.  You have powers we need.  We have knowledge on their location, firepower of our own and two captives.  We'll only pull this off if we work together}.''



``Putting our lives in your hands,'' Miss Militia replied.



``\emph{Only as far as we'd be relying on you,}'' I answered her.



``Who are you, Skitter?''  Legend asked.  He floated closer to my swarm-decoy.  ``I can't get a read on your personality or motivations, and that's without touching on what came up at the close of the Endbringer event.''



``\emph{My teammate is in the hands of the Nine, they could be murdering more people right this second, and you're talking about me, of all people}?''



``If we're going to offer you help, we should know who we're interacting with,'' he said.



I glanced at Trickster, then back at the image on the screen.  ``\emph{What do you want to know?}``



``We've talked with the people in your territory.  Between what they say and what came out at the hospital, I can't help but wonder at your motives.''



``\emph{There's someone specific I want to help.  If I can improve the lives of others at the same time, then all the better.}``



``So where do you stand, then?  Where do you see yourself in terms of the sliding scale of good and evil, heroes and villains?''



I almost laughed, and some of my humor must have translated in a mental direction to my bugs, because they started making a noise that wasn't speech.  I stopped them.  It wouldn't have sounded much like laughter anyways.  ``\emph{All of the above?  None of the above?  Does it matter?  Some of us wear the villain label with pride, because they want to rebel against the norms, because it's a harder, more rewarding road to travel, or because being a `hero' often means so very little.  But few people really want to see themselves as being bad or evil, whatever label they wear.  I've done things I regret, I've done things I'm proud of, and I've walked the roads in between.  The sliding scale is a fantasy.  There's no simple answers.}``



``There can be.  You could do what's right.''



I was getting an inkling of what Bitch referred to as `words'.  Prattle that meant so very little in the face of what was happening in the present.  Was this the kind of irritation, impatience and anger she felt with so many social interactions?  I clenched my fist. \emph{ ``Speak for yourself.  You want to hide here while my group and Hookwolf deal with the brunt of the Nine's attention.  Just like you did with the ABB.}``



``That happened under Armsmaster's leadership.  You can't blame us for being intelligent about how we go about this.''



I was disappointed my swarm couldn't convey my anger.  ``\emph{I can blame you for being cowards.  I'm going.  If you want to talk about morality, start by talking to Armsmaster.''}



``Can't.  He's gone.''



I paused.  Did the Nine get him?  ``\emph{Dead?}``



``Escaped from his hospital room.  With our attention on the Nine, we don't have the resources to track him down.''



``\emph{Does he know about the Nine's threat to hit the city with a plague if he leaves?}``



``I hope so.''



\emph{Fuck}.  Not only was that one more uncertainty stacked onto everything, but Armsmaster was the closest thing I had to a nemesis.  Having him running around the city was not a good thing.



For a brief moment, I contemplated having Trickster teleport me to ground level, so it was \emph{me} talking to the local heroes, and not just my swarm.  I could tell them that I was putting my well-being in their hands, risking them arresting me, as a gesture of good faith.



Except I couldn't help but see myself from their perspective.  Warlord of the Boardwalk.  I'd rotted off Lung's manhood and carved out his eyes.  I'd played an undefined role in Armsmaster's downward slide.  I'd robbed a bank, terrorized hostages with poisonous spiders, attacked their headquarters and used insects dipped in capsaicin to cripple their junior heroes with incapacitating pain.  All the while, I'd acted with a seemingly ambiguous morality.  Was I a good guy doing all the wrong things?  Or did they see me as dangerous and unhinged?



There was no way I could put myself in their hands without knowing what they thought about me, and frankly, \emph{I} wasn't sure how to think about myself.  How the hell were they supposed to make a call?



``\emph{So.  You in?}''  I tried, instead.



I could see him look back at Miss Militia, who shook her head.  ``Miss Militia runs the local team, so it's ultimately her call, but\ldots we've talked about it, and I agree with her.  No.  The risks outweigh the potential benefits.''



My heart sank.  ``\emph{Then one final tip.  You should know that Bonesaw's done some surgery on all of her people.  Implanted protection for the more vulnerable parts of their bodies.  They're tougher than they look.}``



``Thank you,'' Legend said.  ``You might not believe me, but I wish you the best of luck.''



I snarled as I shut the laptop and turned away from the scene, calling my swarm back to me.



``That didn't work,'' Trickster said.



``No.  And we just wasted a lot of time.''



``We'll have Shatterbird working with us, thanks to Regent, and we've got Imp as our man on the inside, maybe.  We're going to outnumber the remaining five or six of them, right?  It's not hopeless.''



``They'll be \emph{ready} for us.  They're entrenched, they have a hostage, and we're totally unable to fight two of them.  How long is it going to take to extricate Grue from whatever cage they have him in?''



``It's not hopeless,'' he repeated.  ``Whatever they're doing to keep Grue prisoner, if I can see him, I can free him.''



``I wouldn't be so sure.''



``Would it reassure you to know that your conversation with the local heroes gave me an idea of my own?''



My head snapped in Trickster's direction.



``Come on.  We should hurry,'' he said.





