





``I was a lot more comfortable with the risky plan when it was something I thought of,'' I said.



``You said calculated recklessness, right?''  Trickster asked.



``Part of that `calculated' bit is control.  Keeping the chaos to a minimum, so we can anticipate and plan.''



Trickster leaned against the door of the vehicle.  ``That may be a bit of a problem.''



``You think?''



The truck passed over a pothole.  Our teams were out in force, our members divided across three trucks.  I rode with Trickster, Sundancer and Tattletale.  Regent and Ballistic were in the second vehicle.  Bitch and her dogs rode in the third.



This was Tattletale's first time venturing out of Coil's base in a little while.  Her power was limited when she could only get information by what we communicated to her, and this was the kind of situation where we needed her at full strength.  If nothing else, it felt better to have another teammate on the field with us, with Grue's absence.



``Sorry,'' I said, ``I don't mean to sound ungrateful.  I know Grue isn't your teammate.  You didn't have to come to help.''



``We're all in this together, right?'' Trickster said.  ``You mind if I smoke?''



I shrugged and Tattletale shook her head.  He rolled down the window and lit a cigarette, placing it through the mouth-hole of his hard mask.



That would be his way of dealing with stress.  We were all tense, and we all had our ways of coping.  Trickster smoked and stared off into the distance.  Sundancer fidgeted.  She frequently realized what she was doing and forced herself to stop, only to pick up something else.  Her leg would bounce in place, then she would stop doing that and start drumming her fingers on her kneepad in some complicated pattern.  It made me think of a pianist or a guitarist fingering the strings.  Tattletale watched people, her eyes roving over the rest of us.  Her cheek bulged slightly where she touched the tip of her tongue against the backside of the wound Jack had left her.



And me?  I retreated into my headspace, I supposed.  I was maybe similar to Tattletale in that I took note of each of the others, but my thoughts were less about simply observing than about cataloguing and mentally preparing.  What options did we have?  What tools, weapons and techniques did we have at our disposal?  Who was going to be backing me up during this operation, and how reliable were those people?



It was constructive, maybe, but exhausting.  There were so many angles to consider, and the stakes were high.  Brian's life, Brian's \emph{quality of life}.  The rest of us weren't in the Nine's clutches, but it would take only one mistake before any one of us could be in the same boat, wondering just how horrible things were going to get for us.



Maybe fatigue factored in, but the more I thought on our allies, the less secure I felt.



The information Cherish had volunteered about Coil, true or not, had left me with lingering doubts.  I was also acutely aware of the distinct lack of chemistry and camaraderie among the Travelers.  They were keeping secrets, with no promises of divulging the information in question.



The last time we'd all been in a car with Trickster, he'd noted that there were \emph{two} major problems that Coil was helping them with.  Noelle was obviously one.  A part of me could buy that there was something serious going on with her, something that necessitated the help of someone like Coil.  Another nagging part of me was thinking that there were still too many unanswered questions.  What was holding them together as a group?  How fragile was that tie?



Was this really what I needed to be dwelling on?



I thought over my arsenal and the options I had with my power.  I'd developed enough techniques that I was starting to have trouble keeping track of them all.  Should I name them?  It seemed like something out of a kid's show, shouting out the names of the abilities as I used them.  `Firebug attack, go!'  `Silkwrap Strike!'



I shook my head a little.  I \emph{was} tired.  My mind was wandering.  I couldn't remember the last time I had more than five hours of sleep, and I'd barely slept at all last night.  Fear and adrenaline usually clarified things, so it probably said something that I was feeling a little dazed despite what we were going into.  Some of that was the constant aggression.  Since the Nine had made their presence known, I'd barely been able to relax and let my guard down.  After Mannequin had started killing people in my territory, taking even a moment to myself made me feel like I was insulting their memories, that I was failing the next batch of people who would become victims of \emph{my }enemies.



``We should stop here,'' Tattletale said.



That was apparently order enough, because the driver pulled over.  The long seconds of stillness after the truck had stopped said volumes.  We didn't \emph{want} to get out of the car, we didn't want to face the Nine, deal with their traps as we tried to catch them in our own.  Two or three seconds passed with tension thrumming in the air, every one of our nerves on edge, ready to act, react, even now.



The sound of a slamming door from one of the other trucks was the little push we needed to move.  We climbed out of the truck and joined the others.  Bitch had been the first one out.  She had Sirius, Bastard and Bentley with her.  We ventured over to a fallen section of wall, peering over it to get a better glimpse of what would be the battlefield.



The final two members of our group arrived a moment later.  Shatterbird landed, stumbling, and Genesis began to materialize in a massive form.



We were close to the site of our last fight.  The Nine had been on their way to Dolltown, and we'd ambushed them, divided them, and then provoked them into extending out of position.  Having done that, we'd kidnapped Shatterbird as she lagged behind and then looped around to capture the wounded Cherish.



Now the Nine were inside Dolltown.  I could only hope the noise and fighting of our last encounter would have given most of the residents the time and the motivation to run.



``How's she handling?'' Tattletale asked Regent.



``Not the easiest power to use,'' he muttered.  ``It's not a physical power, so I'm learning to use it from scratch.  Doesn't help that she's really, really, \emph{really} pissed off.  I think she's a serious control freak.  My control's slipping a bit.''



``How much is it slipping?'' I asked.  ``Is there a chance you'll lose control of her?''



``Always a chance.  But I think I'm okay, so long as she and I remain pretty close to each other.''



``Tattletale, Where are they?'' I asked.



Tattletale pointed at a squat building a few blocks away.  It had the look of a small library, maybe, or a hardware store.  A place meant to accommodate a lot of people for one job. ``Somewhere in there.''



``Then we wait,'' Trickster said.  ``And we cross our fingers.''



Waiting.  The last thing I wanted to do.



Using my bugs, I tried to scope out the area.  \emph{Please don't let there be people here}.



There were.  I had to be subtle, not giving the Nine any reason to suspect I was around, but even if I counted only the people who had bugs on them already, there were far too many people in and around Dolltown.



``Regent, can you stop Shatterbird from listening in?''  I asked.



``Sure,'' he said.  Shatterbird shut her eyes and covered her ears with her hands.



I asked, ``Tattletale, do you know where the Nine are, specifically?''



She shook her head.



``There're people here.  I'm counting thirty or so, but there could be twice that many.  I haven't even taken a serious look at the building the Nine are in, because I don't want to alert them.''



``Ignore them,'' Trickster said.  ``This is risky enough without splitting our focus.''



``If I know where the Nine are, I can tell these people where to run, give them a chance.''



``It's not worth the risk,'' Trickster stressed.  He glanced at his teammates, ``There's still five or six of the enemy in the area.  If they see what you're up to and get any advance warning we're here, this all goes balls-up, and we suffer for it.  Grue dies for it.''



Regent nodded in agreement.



I looked at the others for help.  Tattletale remained quiet, and Sundancer, the one other person I'd hoped would be sympathetic, looked away.



``Those are people,'' I said.  ``Real people.''



``So's Grue, and so are we.  We look out for ourselves first.  If we can take out members of the Nine, we'll save more people in the long run.''



``The ends justify the means?  You realize that when this all goes down, they're going to die?  Almost guaranteed?''  I'd directed Sundancer to attack a group of people who included bystanders, but they'd been goners already, dead for all intents and purposes.  This was something else.



``Thirty people for the sake of hundreds.  It balances out,'' Trickster said.  ``\emph{If} we stick to the plan and \emph{if} we're successful.''



``I can't agree with that.''



``Then make your call.  If you're absolutely certain you're not going to fuck us over and give away the plan, if you're \emph{positive} that the lives you \emph{might} save are worth risking our lives and Grue's, you can go ahead.  You don't have anyone's support here, and it's all on you if you fail.''



Tattletale spoke, ``If you're going to do something, you better do it fast.''



She pointed, and every pair of eyes in our group turned to look.



Purity streaked across the sky, followed by Crusader and a floating rock carrying a whole contingent of their group.  The rest would be moving along the ground.



``Shatterbird, Genesis, go!''



Shatterbird took flight, calling up a storm of glass shards to accompany her.  She flew low to the ground, relying on the surrounding buildings and ruins to keep out of sight.



Genesis had finished pulling herself together.  Her form resembled Crawler, but with some additions.  Growths on her back resembled Bonesaw and Jack.  She tested her limbs, then looked at us.  At me?  I couldn't tell.  She had too many eyes to tell.



Then she ran, stampeding off.  Not quite as graceful as the real Crawler, but that was one more area where we just had to cross our fingers and hope she could sell the ruse.



There was the dull rumble of a distant impact as Purity opened fire on Genesis.  Genesis dodged into a nearby alleyway, leading Purity and the rest of her group off to one side.  Shatterbird fired on Purity and her allies, guiding a torrent of glass shards toward the incoming enemies.  Not enough to kill, or even to maim.  It was enough to hurt and to piss them off.



Coil had informed Hookwolf's contingent about the general location of the Nine.  Sure enough, they'd gathered, girded themselves for battle and marched on, hoping to overwhelm through sheer firepower and force of numbers.  Odds were good that it wouldn't work.  It hadn't in the past.



But, we were hoping, it would put the Nine in a position where they had to decide whether to hold their position or respond to the immediate proximity of this many enemies.



Shatterbird and Genesis were tasked with distracting Hookwolf's forces and preventing them from mounting a direct attack on the Nine's real position.  We couldn't save Grue if Purity leveled the building.



So much hinged on how the next few moments played out.



``The Nine are distracted.  I'm going to help the people run.''



The lack of response was as damning as anything they could have said.



I waited until Purity fired again, then used the rumble as an excuse to stir various bugs into action.  I did a body count, placing bugs on people's right feet, trying to calculate how many there were and how they were distributed.



There was a crowd inside the building with the Nine.  People huddled in a room with Crawler, who lay on the ground with his chin resting on his forelimbs, facing them.



I couldn't find Grue.  Was he in that group?  No.



On the other side of the building, four people were gathered at one window.  A grown man, two grown women, one of whom was nude, and a child.  A man clad in hard armor crouched in one corner, working with tools.  There were enough cool bodies around them that I would've known who they were even if the body types hadn't fit.



``Found them,'' I said, pointing, ``They're watching.''



``They're not stepping outside?''  Trickster asked.



I shook my head.



``Damn.''



I could see Menja leap from Rune's floating rock and grow as she fell.  She was nearly thirty feet tall when she landed, the road cracking under her weight.  Rune leaped off the rock and landed on the husk of a building that hadn't survived Leviathan's attack.  A few seconds later, a large section broke off and lifted into the air.  She didn't stay on top of it for long, choosing instead to gather more ammunition, moving on to other ruined walls and sections of building.



This would be a balancing act.  Unless the Nine didn't plan on defending themselves or running, there would be something of a sweet spot.  A point where the enemy forces got close enough that the Nine were forced to act, yet not so close that anyone else was endangered.



Now that I knew where the Nine were, I could focus on the civilians.  I drew out messages for everyone who was hiding in their homes, along with arrows pointing them away from the Nine and Hookwolf's army.  If someone decided they didn't want to move, I nipped them with a biting insect or two to prod them.



Dozens of people made their way to safety, following my instructions and running for their lives as they headed out back doors or out of windows to avoid being seen.



There were still way too many people in the room with Crawler.  And I still had no idea where Grue was.  Slowly and carefully, I navigated my bugs through the rooms of the building the Nine had occupied: A makeshift dining hall with a kitchen, a room solely for storing garbage, then a small open shower with three stalls.  It had been some sort of office building with no computers, desks or cubicles.



Something big, firm and formed of cloth\ldots one of Parian's stuffed animals?  It lay prone on the ground, on the other end of the building from where the Nine were poised, so large and fat that it wouldn't be able to fit through any of the doors.



I found another cluster of people on the top floor.  Three adult women and two children that ranged from toddler age to five feet or so of height.  Damn it, why did there always have to be kids?



``I can't find Grue.''



``He's in there,'' Tattletale said.



``How sure are you?''



``Pretty darn sure.''



``Then how long before we can move on to the next phase?'' I asked.  ``I found some people, which solves one problem.''



``As soon as the Nine act,'' Trickster said.  ``Tattletale?''



``They're not wanting to move.  Something about the hostages.''



``Hookwolf doesn't care about hostages,'' I told her.



``I know!  But the Nine are still holding back.''



``Regent--'' I started.



``Don't distract me,'' he said, rushing through the words, ``I can barely dodge all this shit they're throwing at me.''



I followed his line of sight to Shatterbird.  Purity opened fire, and Shatterbird used a cone of glass to block the worst of the kinetic energy and refract the light.  Or something.  It didn't work that well.  Shatterbird was knocked to the ground.  She managed to take flight just in time to avoid Newter, trapped the boy in a cage of glass shards, and then flung a barrage of tiny glass shards at Purity and her group.  I could see the glints of the shards catching the light as it flew through the air.



``Draw some fire towards the Nine's location, if you can,'' I said.



``I said don't distract me!''



But he listened.  Shatterbird interposed herself between Hookwolf's advancing group and the building holding the Nine and their hostages.  Purity fired, and again, Shatterbird's glass couldn't absorb the full brunt of the hit.  She was hammered down into the ground again, and what didn't hit her struck the building, not far from where the Nine were peering through the window.



``Come on, come on,'' I whispered.



The Nine reacted.  It just wasn't what we'd hoped for.



Crawler stood and rumbled some words my bugs couldn't make out, and the hostages fled.  The Nine made no move to try to stop them.  Just the opposite.  They revealed why they'd kept them on hand.



The hostages made their way out the doors and into the streets surrounding the building.  Purity was so distracted by Genesis and Shatterbird that she didn't seem to notice what was happening at first.



Tattletale watched with her binoculars.  ``Oh no.''



``Oh no?''  Trickster asked.



Tattletale looked at me, ``Track their movements.  The Nine!  Don't lose sight of the Nine!''



The hostages scattered in every direction, and some invariably headed towards us.  I saw what had concerned Tattletale.  Even though I knew where the Nine were, I was still caught off guard.



Bonesaw's talents apparently included crude plastic surgery.  If `crude' was even the right word.  Every hostage wore the appearance of one of the Nine.  The group that headed towards us had three Jacks, a Siberian and a Bonesaw.  Their expressions were frozen, their eyes wide with terror.  None of them were perfect, one was too heavy in physique to be Jack, and the Bonesaw had apparently been a short-statured woman who'd had her shins and forearms sawed to a shorter length and reattached.  The resemblance was close enough that someone could mistake them for the wrong person at a glance, and that was all the Nine needed.



``Decoys,'' the word was hollow as it left my lips.



``And the Nine are moving out,'' Tattletale reported.  ``Leaving the front of the building.  Get ready!''



I used my bugs to draw a message for the people still hiding in another part of the building.



Crawler was the first to leave the building, charging out the front door, plowing through one or two of the Nine, and barreling towards Hookwolf's army.



The other members of the Nine headed out.  A real Burnscar, Jack, Siberian and Mannequin at the tail end of their mass of fleeing decoys.



``Bonesaw's not leaving,'' I said.



``Doesn't matter!  Now!''  Tattletale shouted.



Trickster hurried to my side, binoculars in hand.  I pointed, and I could feel a pressure building around me.  It was slower than his other teleports, more jarring.  It didn't matter.  Our group was soon indoors.  Me, Tattletale, Trickster, Sundancer and Ballistic.



The interior was rank.  They were smells I'd gotten to know since Leviathan's attack.  Blood, death, and the dank smell of sweat.



Trickster had replaced all of the kids and the three adults that had been accompanying them.  He hadn't brought Regent, because Regent was focused on Shatterbird.  That was part of the plan.  Leaving Bitch behind wasn't.  I could understand it if it was because of a lack of mass to swap with, but my doubts about the Travelers and about Trickster specifically led me to ask, ``You figure Bitch will cover our retreat?''



``And if one of the Nine is here,'' Trickster said, his voice low, ``We don't need her dogs making noise.''



``Right.''  Okay.  Made sense.



I led the way, as I had the best sense of the layout.  Bonesaw was excitedly pacing back and forth.  The rest of the place was quiet.  ``There's only a few places Grue could be.  Confined spaces my bugs couldn't get to.''



``Makes sense that they'd improvise a cell to contain him,'' Tattletale said.



I nodded, swallowing.



Worn and damaged posters and fliers referred to yoga and pilates classes.  Makeshift signs and notices had been raised since this building had been used for the rich-person exercise classes.  These were more pragmatic, detailing chore schedules, contact information and watch rotations.



These people had been getting by, maybe in the same way I'd been trying to get my own people organized.  I felt a growing outrage at what had happened here, what had happened to my people.



\emph{Why?  What purpose did this chaos serve?}



We checked a small sauna.  No luck.  No less than three storage rooms, sealed tight to keep vermin out, turned up empty.



The place I'd mentally labeled the dining hall turned out to be something of a restaurant.  More notices about food rationing covered menus and signs advertising healthy eating.



I headed around the long counter and into the kitchen.  Crates of supplies had been opened, the contents sorted into piles.  There were also other supplies that didn't look regulation.  Several 5-gallon jugs of water that were designed to fit into water coolers were stacked in one corner, and neither I nor my bugs had seen any water coolers in here.



I stopped outside the walk-in freezer and stared at the handle.



``Skitter?''  Tattletale asked.



``There's only three places left where Grue could be.  The other two places are the regular fridge over there and a closet in the basement that I think is too small to hold him and still let him breathe.''



``So if he's not in here\ldots''



``Right,'' I said.  ``Trap free?''



``As far as I can tell,'' she replied.  ``No, if they were going to trap it, they'd lock it first, chain it shut.''



Swallowing, I gripped the handle and hauled the door open.  It took me a second to process what I was seeing.



Brian was in there.  And he was alive.



I couldn't have been unhappier at that realization.



There was no power to the walk-in-freezer, so it was warm.  The interior was maybe ten by twelve feet across, the walls were metal, with racks on either side.  Brian was hanging by the wall at the far end, propped up enough that his shoulders were pressing against the corner bordering the wall and the ceiling, his arms outstretched to either side like a bird hung up for display, his head hanging forward.



It was some sort of collaboration between Bonesaw and Mannequin.  He'd been partially flayed, the skin stripped from his arms and legs and stretched over the walls around him.  His ribcage had been opened, splayed apart.  An improvised metal frame held each of his internal organs in place, some several feet from their intended position, as if they were held out for display, others placed on the shelves of the freezer.  Cases covered in a ceramic shell seemed to be pumping him full of water, nutrients and other fluids that must have been helping keep him alive.



His head was untouched.  He looked up at us, and he looked harrowed.  The look in his eyes was more animal than person, his pupils mere pinpoints in his brown eyes.  Tiny beads of sweat dotted the skin of his face, no doubt due to the warmth of the room, but he was shivering.



``Oh.''  My voice was a croak.  ``Brian.''



I took a step forward, and he seized up, his entire body twisting, his hands clenching, eyes wrenching shut.



``Get back!'' Tattletale gripped me by the shoulder and forced me out of the freezer.



``I- what?''  I was having trouble processing.  ``Trap?''



Tattletale had a dark look in her eyes.  ``No.  Look closer at the walls and floor.''



Numbly, I did as she'd asked.  They looked like hairline cracks, spiderwebbing across everything from the walls to the shelving and even the ceramic cases that Mannequin had set up.  Except they were raised, \emph{over} the surfaces.  ``Veins?''



``Exposed nerves.  Artificially grown, connecting from him to the rest of the room.''



I stared up at Brian, and he stared back at me.



There was no way to help him.  I couldn't even get inside the room to try to comfort him in the smallest ways, not without causing him unbearable pain in the process.



Brian moved his lips, but no sound came out.  He tried to raise his head, as much as the ceiling allowed, his eyes raised towards the sky.  There was a cauterised scar just above his collarbone.



``I could make it quick,'' Ballistic said.



``No,'' I told him.



``It'd be a mercy.''



``No,'' I shook my head.  ``No.  We have options.  Panacea--''



``Is nowhere to be found,'' Tattletale told me, ``And given what happened with Mannequin, she's going to be as far as she can get from downtown.''



``Then Bonesaw,'' I said, clenching my fists.  ``Bonesaw can fix him.''



``She's not going to fix him.  I doubt she'd do it on pain of death,'' Tattletale told me.  ``Skitter--''



``We'll try,'' I told her.  ``At least try.''



I looked at the others.  Sundancer was on the other side of the kitchen, hands on the edge of the sink.  Ballistic had his arms folded.  Trickster leaned against one counter, silent, not looking at the scene.



``Every second you make him go on like this is cruel,'' she said, her voice hard.



``So is every second you spend arguing with me.  I'm not negotiating, here.  I'm willing for him to suffer if it means there's a \emph{chance }we can help him.''



She met my eyes, looking like she wanted to slap me, yell at me, or both.  ``Fine.  Then let's hurry.''



I gave Brian one last look over my shoulder before I hurried off, leaving him behind.  The others followed.



I was using my bugs to track the positions of the Nine, where Siberian and Crawler were in the thick of the enemy.  Mannequin apparently wasn't aware of my presence, so I had my first real opportunity of tracking his movements as he scaled walls and disappeared into manholes to emerge half a street away.  Burnscar used her fire to bombard the enemy and divide them.



Jack was more pragmatic, striking from hiding, threatening his decoys to get them to run out of cover and draw enemy fire, and using every hiding space that was available.  He was quick, smart, and devastating in how he operated.  No movement was wasted, and every time he emerged from cover and swiped his knife, \emph{someone }suffered for it.  As far as I could tell, he was evading Night and Fog.  My bugs could detect some noise from him that I was parsing as a mocking laughter.  Maybe my imagination.  \emph{Probably} my imagination.



I was getting a sense of what Brian had described, once upon a time; that anger and outrage that didn't even come close to connecting with a fire inside, with burning rage or anything like that.  It was cold, dark, and numb.



We found her in one of the exercise rooms.  Yoga mats had been stacked together to serve as mattresses, forming a kind of sleeping area.  Most of the Dolltown residents who had been living in this facility were dead now, their cold bodies lying in pools of blood.  One of the culprits was at the window, clutching the frame. \emph{ Bonesaw}.



I gathered my bugs, directing them her way.



``Wait!''  Tattletale cried out.



I turned to see her stagger.  I whipped around to see Bonesaw.  She was whirling around in response to Tattletale's shout, her eyes wide.  There was a chain stretching from her wrist to the base of the window.



\emph{Not Bonesaw.  Decoy}.



Tattletale crashed to the ground, followed soon after by Trickster.  Sundancer and Ballistic crashed to the ground a second later.



``Why won't you go down!?''  The voice was petulant.



I followed the voice and saw one of the corpses move, rising to its feet.  Bonesaw unzipped the covering of dead flesh she'd covered herself in and shucked it off.  She was wearing a yellow sundress and yellow rubber boots with a short blue jacket, but her hair and each article of her clothing were stained dark brown with the blood that had been on the corpse.  A small tube was in one of her hands, ``I shot you with three darts!  It's rude!''



I glanced down.  Three pea-sized darts with flesh-toned feathering were stuck in the fabric of my costume.  One in my dress, one in a panel of armor on my chest, and another in the side of my stomach.



``Bonesaw,'' I growled.



``Skitter, was it?  Bug girl!  I really want to find out how your power works!  I'll take your brain apart and find the mechanism so I can copy it!  Is your costume spider silk?  That's awesome!  You know the right materials to work with!  No wonder my darts didn't work!''



``What did you do to them?''



``Paralyzed them, obviously.  Living flesh is so much easier to work with.''



\emph{Paralyzed.  }I glanced at my teammates.  \emph{Why couldn't I have finished their costumes?  }Stupid.  I'd spread myself too thin.  I should have finished one costume, then moved on to the next.  Maybe then I would have saved \emph{someone}.



``Oh, and I dosed them with a little something extra.  Because Jack said there's no point in doing anything halfway.''  She gave me a sage nod, as if sharing some universal truism.



``You're going to give them an antidote to whatever you injected into them, then you're going to go to Brian and you're going to fix him.''



``Brian?  Oh!  You mean the boy we put in the freezer!  I'm still trying to figure out where his power comes from.  The darkness comes from inside him, but what's the \emph{source?}  Besides the usual, I mean.  So I took everything apart to see, but he wasn't cooperating.  I told him I'd make the pain stop forever if he would just show me, but he was so stubborn!''  She stamped one foot.



I'd let Brian's name slip.  \emph{Dumb, dumb, dumb.}  I wasn't thinking straight.



``But no, I'm not going to do that,'' she said.  ``I don't censor my art because it offends people.''



``I could convince you,'' I told her.  My swarm flowed forward, and she backed away.  Her eyes, one green and one blue, flashed as she took in the breadth of the swarm, the composition of it.  She was probably already brainstorming some solution.



I wasn't going to give her a chance.  I drew my weapons, one in each hand, and charged through the swarm, straight for her.



My bugs served to give me a half-second of early warning as they felt her jam one hand into the side-pocket of her dress.  I turned on my heel, the burn on my leg screaming in pain as I did it, and threw myself to the right as she brought one hand to her mouth and blew a billowing cloud of powder into the space I'd been occupying.



I got my feet under me and lunged forward again.  I didn't get two steps before I was tackled to the ground.



It was a mechanical spider the size of a large dog.  It had been folded up inside one of the bodies.  Its legs latched around me.  There wasn't much strength in them, and even with my less than fantastic upper body strength, I managed to pry the first two legs apart.



I had \emph{almost} got the spider off me when another caught me from behind.  A third and fourth caught me an instant later, seizing my head and shoulders and my legs, respectively.



Bonesaw exhaled a second cloud of dust into my face.



I held my breath for as long as I could, but there was a limit.  When I did breathe, my chest seized up, and my ears immediately started ringing violently, a headache settling into place.  The muscles in my arms and legs locked up.



She sprayed an aerosol around herself, killing my bugs.  Not that it mattered.  My facility with my power was getting clumsier and clumsier as the headache increased in intensity.



\emph{No, no, no, no, no, no.}



``Bring them,'' she said.  The mechanical spiders leapt to obey.  Within moments, me, Tattletale, Trickster, Sundancer and Ballistic were being dragged inch by inch towards the dining hall.  Towards Grue.



\emph{No, no, no.}



It took long minutes for us to get there.  I could hear faint rumbles of the ongoing battle and Bonesaw's humming.  It was all I could do to keep breathing.  It was like my body had forgotten how, and it demanded my constant attention to maintain that simple rhythm.



With the aid of her spiders, she stacked us like logs.  Ballistic and Trickster went on the bottom.



I couldn't even grunt as the spiders leveraged me onto the pile alongside Tattletale.  I stared down at the mask of the third person below us.



\emph{Imp.  She'd got Imp.}



Bonesaw crouched so her face was level with mine.  ``This is going to be fun.''





