





``With the shoulder bone connected to the,'' she paused, ``Hip bone\ldots''



Bonesaw sang to herself as she drew a scalpel from her sleeve, investigated it, then laid it on the counter.



``And the hip bone connected to the\ldots back bone.''



She drew a pair of forceps from beneath her dress, another two pairs of forceps were retrieved, joining the first.



``And the back bone connected to the\ldots knee bone.  And the knee bone connected to the\ldots hand bone.''



I was scared.  I could admit that.  I could barely think straight, I couldn't move, and whatever she'd dosed me with was rendering me unable to use my power.  It was \emph{there}, it wasn't like what Panacea had done; it hadn't shut it down entirely.  I could sense what my bugs did, and I could maybe give them crude instructions, but I couldn't do anything even remotely complicated or delicate.



``And the neck bone connected to the--'' She rocked her head to either side as she finished, ``Head bone.''



I could see the open door of the refrigerator out of the corner of my eye, but couldn't turn my head to get a better look.  Brian could see us from where he hung.



I didn't want to go down without a fight.  I couldn't give specific directions to my bugs, but if I tried, maybe I could give one.  Maybe, just maybe, I could rely on my subconscious to guide them, even if my conscious mind wasn't up to it.



I controlled my breathing, \emph{in then out}, and gave the order.



\emph{Attack}!



If the commands could be analogous to words in my head, this was a shout.  There was no control, no guidance or direction.  I didn't have the facility.  Still, every bug in reach, within a range of five or so city blocks in every direction, began to converge on our location, veering towards Bonesaw.



She noticed almost immediately, drawing the can of aerosol spray she'd used to wipe out the first swarm I'd set on her.  One hornet managed to sting her, and with my power as limited as it was, I couldn't stop it from contracting its body in such a way as to inject its venom into her.  I wouldn't have if I could.



The rest of the bugs died on contact with the spray, their bodies shutting down.



Except my order was a continuous directive, much as my calling my bugs to me had been when I'd passed out while fighting Bakuda.  It worked on its own, without my direction.  It was eerie to track their movements, to see just how much initiative they took without my conscious mind guiding them.  They spread out, navigated past obstacles, they organized into ranks and tried to attack her from behind, while she was spraying the ones in front of her.  Some of the flying insects were even dropping spiders onto Bonesaw.



``This is annoying,'' I heard Bonesaw comment.  I couldn't see her in my field of view, which was primarily limited to the floor, Imp's mask and if I looked as far to my left as I could manage, the fridge that held Brian.  Few of the bugs were getting past that spray, and even the droplets of the spray that had settled lingered on Bonesaw's skin, hair and clothing were enough to kill or incapacitate them on contact.



I was unable to respond to her statement.  I focused on breathing, and taking in every detail I could.  My eyes could still move, my fingertips could twitch, but nothing else.



``Just so you know, I've rendered myself immune to all those pesky little venoms and allergens,'' she said.  ``And I can turn pain off like I'm flicking a switch.  Don't want to do that on a permanent basis, but it does make this easier to deal with.''



So I wasn't even hurting her.  Damn it.



``It's still \emph{annoying}.''



I could feel my bugs congregating on her as she put the aerosol down and fumbled around inside her pockets.  Test tubes: I could feel the long, smooth glass. She dropped something into each, then stabbed the aerosol can.  The smoke that plumed out killed most of the bugs in the area.  I couldn't follow what she did with the can and the test tubes.



``It's interesting,'' she said.  I felt small hands on me, and she heaved me over so I was staring at the ceiling, and at her.  Clouds of what looked like steam were rising around her.  From the test tubes?  It was having the same effect on my bugs that the aerosol had.  She'd erected some kind of gaseous barrier.



``See, there's this part of the brain that people who study parahumans call the Corona Pollentia, not to be confused with the Corona Radiata.  It's a part of the brain that's different in parahumans, and it's the part that's used to manage powers, when the powers can be managed.  More specifically, there's this part of the Corona they call the \emph{Gemma}, that controls the \emph{active }use of the power, the same way there are parts of the brain that allow us to coordinate and move our hands.''



She ran her fingers over my exposed scalp, massaging it, as if she were feeling the shape of my head.  ``The size, shape and location of the Corona and the Gemma changes from parahuman to parahuman, but it tends to sit between the frontal and the parietal lobe.  Beneath the `crown' of the head, if you will.  They can't really lobotomize the Corona in criminals.  Some of that's because the location and shape of the Corona depends on the powers and how they work, and trial and error doesn't work with the scary bad guys who can melt flesh or breathe lasers.''



She tilted my head back and felt around the edges of my mask, trying to find the part where she could pull it off.   ``I'm \emph{really} good at figuring out where the Corona and the Gemma are.  I can even guess most of the time, if I know what powers the person has.  And I can pry it wide open, make it so the powers can't be turned off, or I can temporarily disable it, or modify it.  The powder I blew into your face?  It has the same prions I put in the darts I shot your friends with.  Cripples the Gemma, but it leaves your powers intact.  Can't experiment with your abilities if I've fried your whole Corona Pollentia, right?  Right.''



She angled my head and stared into my goggles with her mismatched eyes.  ``Dealio is, the Corona's way too small to be doing what it's doing.  As parahumans, our brains are doing these amazing things.  The framework, all the details our minds are using to decide what works and what doesn't, the sheer potential, even the energy we're using, it's too much for our brains to process, and it's \emph{waaaay} too much for a growth that's no bigger than a kiwi.  All of that?  It's got to come from \emph{somewhere.  }And the other reason you can't just carve out the Corona?  If you do, the powers still work on their own.  The person just can't control them.  It becomes instinctive, instead.''



She began feeling around my mask for a seam, buckle or zipper, searching.  She talked as she grabbed the part of my mask that bordered my scalp and tried to peel my mask down towards my chin.  ``So you can see why I find it \emph{very} interesting that you still have the ability to control bugs, even when your Gemma is out of order.''



She gave up on pulling my mask down.  The armor panels made it too difficult, and the fabric wouldn't tear.  She snapped her fingers, and one of her mechanical spiders stepped close.  She removed one of the tools at the tip of the spider's leg – a small mechanical circular saw.  It buzzed like a dentist's drill as she turned it on.  She began taking my mask apart, thread by thread.



``I'm \emph{ten times} as excited to take your brain apart, now!  You might give me a clue about the passenger.  See, I think it's something that's hooked into your brain.  It was alive up until your powers kicked in, it helped form the Corona, then it broke down.  I've seen it at work when I've provoked and recorded trigger events, seen it die after.  But I'm pretty sure some kind of trace is still there, linked in, cooperating with us and tapping into all those outside forces you and I can't even comprehend, to make our power \emph{work}.''



\emph{Breathe in, breathe out}.  I was having to consciously maintain my breathing.  Whatever her dust had done to me, it had also jammed up the part that handled the more automatic things.  My pounding heart wasn't in sync with the speed of my breathing, and I was beginning to feel dizzy and disoriented.  Or maybe that was the powder.  Or fear.



``But I haven't been able to \emph{find} it.  It's not physically there, or it's so small that I haven't been able to track it down.  If your `passenger' is strong enough to let you work around a disabled Gemma, if your powers work without your say-so, maybe it'll be easier to spot.''



Her progress through the fabric of my mask was slow.  She stopped to clear loose material from around the tool.



``Don't worry.  I'll put your skull's contents back when I'm done looking.  Then we can get to the \emph{real} fun.''



She peeled my mask off.



\emph{Breathe in, breathe out.  Don't want to pass out.  }Or maybe I should?  Maybe I didn't want to be conscious for what came next.



Her scalpel slid across my forehead, so fast and precise that it barely hurt.  I caught a glimpse of her untangling her fingers and her scalpel from my long hair before the first dribbles of blood flooded down into my eyes.  It stung, and I was momentarily blind before I managed to blink the worst of it away.  I wanted to blink more, faster, but the response was sluggish at best.  I couldn't tell if my contacts were helping or hurting matters.



I was put in mind of the incident just days before I'd gone out in costume.  The bathroom stall, the showering in juice.  It had started with cranberry juice in my eyes and hair.  How had I gotten from there to here?



``I can't tell you how excited I am.  It's like Christmas, opening a present!  Thank you!''  She bent down and kissed me squarely in the center of the forehead.  When she sat up, there was crimson all over her lips and chin.  She wiped most of it away with the back of her hand, uncaring.



She glanced at the circular saw, and it started up with that high-pitched whine.



Then it stopped.



``Clogged up with teensy-weensy bits of silk and whatever that armor's made of, too slow.  But don't worry!  I have a bigger saw somewhere else.  I was using it for one of the other surgeries I did earlier.  Let me see if I can find it.''  She stood, then stepped out of my field of vision.  My bugs couldn't feel her, but I \emph{could} tell that she was carrying one of the steaming, smoking vials with her, as bugs died on the other side of the room, then the hallway, then a nearby room.



I tried to move and failed.  My fingertips twitched, I could blink if I focused on it to the exclusion of everything else.  My eyes, at least, moved readily enough.



I couldn't \emph{do} anything.  Even an instruction as basic as `find Bitch' was beyond my abilities at present.



Bonesaw had talked about this `passenger'.  My ally, my partner, after a fashion.  Was there some way to use it?  To put more power in its hands?



\emph{Help!}  I tried, putting every iota of willpower into the command that I could.



Nothing.  Too vague.  Whatever aid my `passenger' provided, it wouldn't think of something I couldn't.  My bugs didn't respond.



It was the perfect time for a rescuer to show up.  My bugs had stopped going after Bonesaw because we weren't aware about her current location, so they hovered in place, clinging to walls and feeling around for people who might be their target.  There was a chance that they would bump into someone else.  If a rescuer was coming, my bugs would see them.



There was nobody.  No people on their way.



None of my teammates were moving, either.



If I had the ability to use my power properly, I might have done something with the smoking vials that Bonesaw had left behind.  Used loops of silk to drag them away, perhaps.  I didn't.  My power was clumsy, now, a brute force weapon at best.



And hell, I was just so tired.  Physically, mentally, emotionally.  So many burdens on my shoulders, so many failures that had cost so much.  We had fucked up here, had underestimated Bonesaw.  I'd gone with Trickster's plan to set Hookwolf's contingent against the Nine and buy us the chance to infiltrate and rescue Brian, even though I'd known the strategy had too many holes, too many unpredictable variables.  I'd been too tired to think of something else, too preoccupied and impatient because Brian was in enemy hands.



I would have resigned myself to a fate worse than death, but how did one do that?  How was I supposed to convince myself to give up?  It would be so easy, on a level.  It was alluring, the idea that I could stop worrying, stop caring, after so much pressure for so many weeks and months.  After so many \emph{years}, if I counted the bullying.  I \emph{wanted} to give up, but a bigger, more stubborn, stupider part of my brain refused to let me.



Bonesaw returned all too soon.  ``Threads, Skitter?  These yours, or leftovers from before?''



Threads?  I hadn't set any tripwires.  I \emph{should} have, but I'd been more focused on a quick rescue mission than preparations for a potential fight.



My bugs felt movement.  Except nobody had entered the building, to the best of my knowledge.  It was in one of the hallways.  Big.



The huge stuffed animal I'd noted in the hallway.



Of course.  Parian's creations had deflated without her power to sustain them, hadn't they?  The stuffed thing was inflated, heavy, so she was here.  My bugs couldn't detect her, but she was here.



``Outlet, outlet, need an outlet.  You'd think there'd be more in a kitchen, but nooooo,'' Bonesaw muttered.  She passed through my field of view, holding a saw twice the size of the one she'd held before.



The stuffed animal moved forward clumsily.  My swarm's contact with it was intermittent as it made its way towards us, then past us, venturing into a hallway.



``Gonna have to cut a hole in your skull, Skitter.  Unavoidable.  I'd go up through your nose, but I couldn't reach the top of your brain with the equipment I have.  Going to make a little window.  Just big enough to get my hand through.''



She turned on the saw, and it screamed, a shrill whine on par with nails on a blackboard, but unending, ceaseless.



The stuffed animal was turning around, coming back down the hallway, towards us.



\emph{Have to stall her}.



I looked up at her, then deliberately blinked three times in a row.



The saw stopped.



``Trying to say something?''



I blinked once, hard.



``Is that one blink for yes, two for no?''



I blinked twice.  Just to confuse matters.



``That's confusing.  You're not just trying to delay the part where I carve up your brain, are you?''



I blinked twice.



``Not getting what you're trying to say.  One blink for yes, two for no, okay?  Now, do you actually have something meaningful to communicate?''



I blinked once, hard.



``Are you going to tell me to stop?''



I blinked twice.  She wouldn't listen if I did, and then it would be right back to the surgery.  I trembled, but I didn't take my eyes off her.



``Tell me when to stop.  Last requests, threats, your friends, um\ldots science, art--''



I blinked once.



``Art?  Yours?  Mine?''



Another blink.  If anything would get her talking, it was her `art'.



``What do you want to know.  About your friend there?  It's more research than anything else.  Or maybe about you?''



I blinked.  The stuffed animal was close.



``Art and you, huh.  You want to know what I'm gonna do when we're done with my investigation?''



\emph{Why not?}  Knowing had to be better than wondering.  One blink.



``I'm going to go all out.  Way I figure it, I set your Gemma lobe to attract bugs around you, then remove it, so you've got no conscious control over it.  But there's a point to it!  I make some physical modifications to you, see.  Implant some of Mannequin's equipment so you've got enough sustenance to keep you going, and sustenance to keep the bugs you bring to you alive.  You become a living hive, see?  We could even make it so they crawl inside you and build nests there.''



The stuffed animal pushed the door open and walked into the cafeteria.  The room darkened as it passed in front of a window.



\emph{Please don't notice it}.



``I've got a regular mod for your amygdala, to make sure you behave, and a frame I implant to your skeleton and heart to help control you, make you stronger, more durable.  I figure we'll try to go for a cosmetic shift.  I have to say I admire this armor, so why not let take that to the logical conclusion?  We'll give you an exoskeleton.  It'd be awesome.  Compound eyes, claws.  We'll see how far we can go.  Won't that be fun?''



The stuffed animal had stopped in the middle of the cafeteria.  Either it didn't hear Bonesaw or something else had its attention.



I could feel that not unfamiliar sensation of darkness creeping in around the edges of my vision.  Was I passing out?  How much blood was I losing?



I blinked three times.  \emph{Stall}.



``No, no.''  She stroked my hair, and my forehead lit up with a burning pain where she'd cut.  ``We should get this done before you drop dead.  Don't think I can't see the changes in your breathing and pupil dilation.''



She started up the saw and pressed it against my skull.  The horror of what she was doing was compounded by the most god-awful noise, and a grinding vibration of my skull.



If it hurt, I didn't register it, because the noise of the tool had drawn the stuffed animal's attention.  It charged for us, slamming through the glass sneeze guard of the dining hall's serving counter.  It struck Bonesaw, hard, and the saw slid across my head, cutting through my hairline.  I didn't care.



My rescuer was some kind of cartoonish dinosaur made of black and blue fabric.  I could see the logo of this health club repeated several times over the stuffed animal's exterior.



Out of the corner of my eye, I could see Bonesaw slowly stand.  The two combatants were at opposite points in my peripheral vision; Bonesaw stood to the far left, Parian's creation to the far right.



``That's \emph{really} rude,'' Bonesaw said, putting inflection on each word.  ``I was having a nice conversation with Skitter, and you interrupt?''



She snapped her fingers, and mechanical spiders leaped from a spot I couldn't see to latch onto the stuffed dinosaur, much as they'd done with me.



Needles, saws, scalpels and drills attacked the dinosaur, and it, in turn, smashed the spiders to the best of its ability.  Though it clubbed the spiders into pieces with its hands, feet and tail, it still continued to march steadily towards Bonesaw, moving over me and the others.



Bonesaw, for her part, was retreating, holding a pair of test tubes in one hand, dropping what looked like color-coded sugar cubes into them with the other.  She glanced around quickly, then lunged for a nearby counter, grabbing a bottle of water.  She upended it over the test tubes, going for haste over precision.  More than half of the water splashed around her feet.



Parian's creation struck the villainess a second time.  Bonesaw was thrown into a metal shelf unit with enough force that she dented it.  One test tube slipped from her fingers.



The other, she whipped at the stuffed dinosaur.  It hit with enough force that it shattered on impact.



The dinosaur struck Bonesaw a third time.  Heavy as the impact was, Bonesaw was cornered and she couldn't go flying as she'd done before.  My view of the scene was limited to the back of the Dinosaur's head, and the occasional view of an stubby-fingered arm as it was drawn back for a haymaker punch.  It pounded her, one hit after another.



My heart sank as I saw the stuffed dinosaur begin to deflate.  It backed away from Bonesaw, and I saw a spreading area on its side where the fabric was thinning out, bleaching.  Once the first holes appeared in the fabric, the rest of the process was swift.  It crumpled almost explosively, revealing a figure inside.



Parian threw off the cloth that had covered her and used her power to rip away her sleeve and part of her dress where it was disintegrating; whatever had eaten at the fabric of her dinosaur armor was continuing the process with her clothing.



I could see Bonesaw too.  Her face was bloodied, her nose gushing blood, and her cheek was a ruined, abraded mess.  Whatever had eaten at Parian's dinosaur had gotten on her too, devouring the edges of her dress, one sock and part of the shoe on the same foot.



``\emph{Rude}.''



``You killed my mom,'' Parian's voice sounded hollow.



``My teammates did most of the actual killing, so I don't think I did, if that makes you feel any better.''



``My aunt, my best friend, my cousin\ldots they were all here.''



``Wrong place, wrong time?'' Bonesaw shrugged.  She slapped at a wasp that had managed to get in position to sting her.  She wasn't in the area of her anti-bug smoke anymore.



``They told me to run, to protect the kids.  But they were supposed to escape while I handled that,'' Parian sounded lost, dazed.  ``I thought they'd get away, so I played dead.  I didn't know.''



She wasn't a fighter, I remembered.  She had held her own against Leviathan, but she didn't have experience.  I wanted to scream at her, to make her stop talking, to do something to Bonesaw.



``If it makes you feel any better, some of them might still be alive.  We didn't kill them all.''



Parian snapped her attention to Bonesaw, ``What?''



``Some we left alive, so I could give them five-minute plastic surgery.  My spiders handled most of it.  Implants under the skin, some chemical dyes for hair\ldots''



``Plastic surgery?''  Parian shook her head.  ``What?  Why?''



``To make them look like us.  They're all running around out there, drawing enemy fire and freaking out.  It's \emph{funny}.  And of course, it'll take a dozen visits with doctors less talented than I to get something even \emph{resembling} their old faces back.  Can you imagine how many people are going to double take when they look at them, before they've all been fixed?  Like, `Oh no, it's Siberian!', except it isn't.''



Parian flung one hand in Bonesaw's direction.  I didn't see what happened next, but the bugs that were still drifting in Bonesaw's direction to attack her were telling me that there were threads stretching between the two of them.  A bug settled on the point of a needle where it had impaled the side of Bonesaw's neck.  Twenty or thirty needles with attached threads extending between them and Parian's sleeve.



Bonesaw crunched something in her mouth, ``You're playing so rough.  Ow.  I think you broke one of my teeth, with your dinosaur.''



Parian ignored her.  A twist of her hands, and Bonesaw was lifted into the air, spread-eagled.  Bonesaw's skin stretched where the needles pulled at it.  Parian advanced towards the villain.



Broken tooth?  No.  When I'd kicked Cherish earlier, hadn't she said that Bonesaw had reinforced her teeth?  Surely the psycho would have done the same for herself.



\emph{She was lying}.



And there was nothing I could do to alert Parian.



Parian picked up one of the scalpels Bonesaw had placed near me.  Her hand was trembling even after she had it in a white-knuckled grip.  ``I don't want to do this.  I never wanted to fight.  But I can't let you walk away.  That's the most important thing.  I'm willing to compromise what I believe in, compromise \emph{myself}, to do that.''



Bonesaw rolled her eyes.



\emph{Wall!  }\emph{Barrier!}



My bugs left Bonesaw's presence to form a barrier between her and Parian, but they were too few.  Too many had died against Bonesaw's bug killing smoke.  Parian ignored them.



In one motion, Parian stepped close and stabbed the scalpel into Bonesaw's throat.  Then she did it again, and again, stabbing over and over, hysterical.



It wasn't enough blood.  I knew it, and Parian had to know it.



Bonesaw spat into Parian's face.  Her own flesh burned as whatever chemical she had been holding in her mouth spilled down her lip.



Parian, for her part, dropped the scalpel, tore her mask off and staggered blindly in the general direction of the sink, her hands over her eyes.



\emph{No}.



\emph{What I wouldn't give for the chance to change this, to act, to offer even one word of assistance.}



Bonesaw turned her head and spat again, some residual chemical directed at the threads. When that didn't achieve the desired result, she repeated the process.  The threads snapped and she dropped to the ground.



``Burned mah tongue,'' Bonesaw said, to nobody in particular.  Or to me?  She stuck it out to demonstrate.  It was scalded, blistered and covered with dead white flesh in much the same way her lip was.  She spat again.



Parian reached the sink, cranked on the tap.  There was no water.  She threw herself to one side, feeling along the counter for something, anything to wash out her eyes.



``You're lucky I'm so nice,'' Bonesaw said.  She lifted up the tattered bottom of her dress to dab at her lip and tongue.  I could make out test tubes, equipment and pouches, all belted to her thighs and stomach.  ``If I was a less forgiving person, I'd make you regret that.''



Parian sagged to her knees, hands still on the counter, heaving for breath.



``But instead, I'll leave you alone to think about what you've done,'' Bonesaw said.  She plucked some of the needles out of her skin.  ``I'll finish with these guys, and later, I can show you what \emph{I }can do with a needle and thread.  It'll be fun.  Common interests!''



``Making friends, Bonesaw?''



\emph{No}.  Any vestige of hope I'd had disappeared.



Jack leaned over the counter.  Burnscar stood beside him, looking troubled.



``Jack!  Yes!  I'm having lots of fun!  These people are so interesting,''  Bonesaw smiled.



``You hurt yourself,'' Jack frowned.  ``Your mouth.''



``The doll-girl ambushed me.  But I'm okay.  I can fix myself after I'm done here.''



``You'll have to finish fast.  We're going.''



``No!''



``Yes.  The enemy's recouping from the first few hits, and they're stalling Siberian and Crawler.  Only a matter of time before they engage in one good flank and blindside one of us three.  We leave now, and all they remember is how hard we hit them and how little they could do.''



``But I have research!''



``Bring three.  We won't be able to bring them all along, and you know they get messy if you leave them like that for too long.''



``Only three?''  Bonesaw pouted.



``Only three.''



``Then, um.  Skitter\ldots''



I felt hands seize my feet and pull me away from my teammates.  Burnscar.  She held me under one arm, my head and arms dangling.  Beads of blood dripped down to the floor.



``Um, um.  Tattletale.  I want to see what her brain looks like, too.''



``Tattletale it is.''



``And Trickster!  Because Ball-of-fire girl killed Hack Job.  I want another.''



\emph{Hack Job?}



``Trickster it is.  Finish off the rest.''



``Can I leave \emph{Brian} there?  I have to show my art to people to get known.''



``Brian, is it?  Hm.  I think that's a very good idea.''



``Yes!  Then we'll go from first to last.  The girl with the horns.''



\emph{Imp?}



The small circular saw started up with its high-pitched whine.



Then it stopped.  I could hear a strangled noise.



``Aw.  Look at his heart beating!  So fast!''



Burnscar turned, and I could tell they were looking at Brian.



Another strangled noise, trying and failing to form words.  It was so forced and ragged that it made my own throat seize up in sympathy.



``You don't want to see your sister die, huh?  That's sweet,'' Bonesaw said.  ``Maybe you should have taught her the basics.  Don't have to see her if she's going to walk straight into a modified wolf trap.  Did you know?  She turned off her power just so she could beg for help.  \emph{From us}.  She's not very bright.''



He made a sound that might have been a growl or a howl of rage, but there was no volume to it, and it was more high-pitched than anything else.



``Don't worry!''  Bonesaw said, ``I'll take good care of your friends.''



I felt a hand pat my cheek.



``Come now, Bonesaw,'' Jack said.



``It's just so funny, watching him react.  His heart beat faster when I touched her.''



``It did.  But we should go.  Burnscar?  Torch the ones we're not bringing.''



``I wanted to!''



``You had your chance, little b.  You got distracted.''



I could feel the heat of nearby flame as Burnscar manifested a fireball in one hand.



Darkness rolled over Burnscar's feet, a carpet.  There was no direction to it, and very little volume.  It pooled on the ground and spread.



``Yes!  He's doing it!  Can I look?  I just want to get the hard drive!''



``No.''



``But--''



I could feel my heart pounding, pounding, then stop.  The pain was gone.  I was gone too.  I had no body, only perception.



The scene was familiar.  At the same time, I couldn't have said what happened next.  It was like a book I'd read years ago and promptly forgotten, too strange to commit to memory.



Two beings spiraled through an airless void, past suns, stars and moons.  They rode the ebbs and flows of gravity, ate ambient radiation and light and drew on other things I couldn't perceive.  They slipped portions of themselves in and out of reality to reshape themselves.  Push further into this reality to ride the pull of one planet, shift into another to ride that slingshot momentum, or to find some other source of momentum elsewhere.  Ten thousand thousands of each of the two \emph{entities }existed simultaneously, complemented each other, drew each other forward.  They shrugged off even the physical laws that limited the movement of light, moving faster with every instant. The only thing that slowed them was their own desire to stay close, to keep each other in sight and match their speeds.  Yet somehow this movement was graceful, fluid, beautiful even.  Two impossible creatures moving in absolute harmony with the universe, leaving a trail of essence in their wakes.



I focused on one of them, and I got the sensation that this \emph{wasn't} a scene I'd seen before.



I could see what it saw.  It was looking forward, but not in distance.  Ten thousand pictures at once.  Seeing situations where it arrived at its final destination.  Earth.  The farther forward it looked, the broader the possibilities.  It was looking for something.  Paring away the branches where the possibilities were few.  An Earth in a perpetual winter.  An Earth with a population of hundreds.  An earth with a population of more than twelve billion, that had stalled culturally, a modern dark age with a singular religion.



And it communicated with its partner.  Signals transmitted not through noise, but wavelengths transmitted across the most fundamental forces of the universe.  In the same way, it received information, it worked with its partner to decide the destination.



It viewed a world, one point in time in the present, and in a heartbeat, it took in trillions of images.  Billions of individuals, viewed separately and as a tableau.  Innumerable scenes, landscapes, fragments of text, even ideas.  In that one heartbeat, I saw people who were somehow familiar.  A young man, a teenager, out of place among his peers, men who were burly with muscle.  They were drinking.  He was tan, with narrow hips, his forehead creased in worry above thick glasses, but his mouth was curled in the smallest of wry smiles over something one of the men was saying.  A snapshot, an image of a moment.



It was my world, my Earth it was looking at.



Coming to a consensus, it transmitted a decision.  \emph{Destination}.



The reply was almost immediate.  \emph{Agreement}.



More signals passed between them, blatant and subtle.  A melding of minds, a sharing of ideas, as intimate as anything I'd seen.  They continued to communicate, focusing on that one world, on the possible futures that could unfold, committing to none, but explored the possibilities that lay before them.



They broke apart, the two massive beings that spiralled together, and I gradually lost my glimpse into what they were thinking, what they were communicating.  Whatever view they'd had of the future, they were losing it.  It was too much to pick through on their own.



\emph{Where have I seen this before?  }I thought.



But somewhere in the course of forming and finishing the thought, I'd broken away from whatever it was I'd seen.  It was slipping from my mind.  The void I was in was not the world of the entities, but Brian's world.  Brian's power.



The darkness coiled around me, \emph{through me}.  It was different, slithering past my skin to brush against my heart, tracing the edges of my wounds, the gouge in my skull that Bonesaw had made with her saw, slithering over and through my brain.



I could feel my power slip just a little out of my reach, my range dropping, my control over the bugs just a touch weaker.



But I could still see through my bugs.  I could still feel what they felt.  They'd gathered for the barrier I'd tried to erect between Parian and Bonesaw, and they'd dispersed in the time since, touching everyone present.  Burnscar had put out her flame, was cradling her hand to her chest.  I could feel Bonesaw and Jack, standing a short distance away.  I could feel Trickster, Sundancer, Tattletale, Parian, Ballistic and Imp.  I could feel Grue, hanging from the wall of the walk-in freezer.



I could feel another person, someone who hadn't been there a moment ago.  A man standing in the darkness.



The man strode forward, uncaring about the darkness.  He caught Burnscar around the face with one broad hand, and he brought it down hard against the counter.  I was dropped to the ground.  Burnscar fell across me, limp and unmoving, and the man flickered out of existence.



The darkness slipped away, retracing its steps through my body, undoing its passage between my organs and joints, through and inside my blood vessels.



A clearing formed.  An expanse of dim light, lit only by one shaft of light that managed to come in through the corner of a window.  Burnscar's head was pulverized, unrecognizable.  She lay limp, unmoving, dead.



``Interesting,'' Jack said, looking down at his fallen teammate.



``Yes!  I'm almost positive I got this on record!'' Bonesaw squealed.



``Which you'll have to leave behind.  We'll retreat.''



``I just need the hard drive!  I've been trying to get data like this for ages, and it's a new system!''



Bonesaw started to head for the walk-in fridge where Brian was, but Jack grabbed her by the back of the neck.  ``No.''



``It's `kay!  Two seconds!  I'll be right back!''  She slipped out of his grip, running into the freezer, opening one of the cases that looked Mannequin-made.



The darkness continued to dissipate around Brian, and I was aware as a masculine figure flickered into existence in the midst of the cloud, in one corner of the walk-in freezer.



It was Brian, but it wasn't.  It was colored in monochrome, with one eye open, the other half-formed.  Markings in white covered his flesh, spiraling out from one pectoral, covering his chest and stomach.  His hands were white to the elbow, and he was sexless.  A ken doll with only more white patterns between his legs.



Or maybe he was white and the markings were in black?



Almost casually, he reached out and seized Bonesaw's hands, which gripped the drive.  He raised her off of the ground, her feet kicking, and she grunted as his grip tightened.



``The things I put up with,'' Jack said, seemingly unconcerned.  He whipped out his knife, slashing at the pseudo-Brian.  There was no effect.  ``Hm.''



Grabbing a meat cleaver from the kitchen counter, he hacked at Bonesaw instead.  It took three swings to sever her arms at the wrists.  She hit the ground running, her stumps jammed into her armpits.  They disappeared over the counter of the dining hall, Jack helping Bonesaw up.



Monochrome Brian lunged after them, but the floor of the freezer shattered beneath one foot.  He lost his orientation, then flickered out of existence once more.



I could see Brian from where I lay, as I struggled to breathe with the one-hundred and whatever pounds that were piled on top of me.  He hung there, haggard, glaring at nothing in particular.  The man didn't reappear, but the stream of incongruent events continued; I could see one of Brian's ribs twitch like the limb of a dying insect.



With a glacial slowness, his body parts began retracting back into place.  The metal frames holding his intestines and organs into place bent, then gave way in the face of the inexorable pull.



It took a long time.  Five minutes, maybe ten.  But his skin crept back, tearing where it had been pinned to the wall, joining back together, then healing.  Even the scratches that had criss-crossed his chest since he'd fought Cricket began to mend.



The healing stopped before it was entirely finished.  I saw the figure appear again.  The monochrome, half-formed Brian.  Mercilessly, it tore out the metal studs that had impaled Brian's limbs to the wall.  It caught Brian, then laid him carefully on the ground.



He couldn't walk, so he dragged himself towards us.



\emph{He had another trigger event}.  Two new powers?  Three, if I counted the way his power was diminishing my own?



He touched my hand, held it between his own.  I could feel something thrumming through me, willing me to take hold of it.



It took me a minute to figure out how.  The exposed bone of my forehead itched, then sang in an exquisite agony as it mended.  My skin was next.  My seized up muscles were last.  My power was last to mend, and I regained my control, though the diminished effect continued.



I clenched my fist, struggled into a standing position.  Brian hurried to Aisha's side, grabbing her.



\emph{Four new powers?}



I hadn't heard about anything like this.



``Come on,'' he said, his voice hoarse, ``Don't have long.  I-  Damn it!''



His darkness flowed out from his skin, heavier than I'd ever seen it, slow to expand, but it seemed to generate itself.  It slithered through me yet again.  Slithered through my \emph{bugs}.



It was minutes before the darkness dissipated.  When it did, Tattletale was standing.  Parian was standing on the other side of the room, eyes wide.  The three Travellers were huddled together.



``What the hell was that?'' I asked.  ``Brian, hey--''



I stopped.  He was on all fours, his head hung, his cheeks wet with tears.



I reached out for him, but a hand seized my wrist.  Tattletale.  She shook her head at me.



While I backed off, Tattletale reached for Imp, whispered something in her ear.



Imp bent down and took off her mask.  In a voice far gentler than any I'd heard from her before, she said, ``Hey.  Big brother?  Let's get out of here.''



Brian nodded, mute.



Aisha could approach him, but I couldn't?



He stood, refusing Imp's offer for help in standing.  He clutched one elbow with one hand, the arm dangling; it wasn't an injury, I was pretty sure.  He'd healed the worst of it.  It was something else, some kind of security in the posture or something like that.



Darkness boiled out of his skin, a thin layer.  It moved slower than it had before, thicker, more like tendrils sliding against one another than smoke.  Just like the arm he had across his chest, gripping his elbow for stability, it was a kind of barrier, armor or a wall erected against the world.  He walked slowly.  Nobody complained, despite the proximity of our enemies and the fact that the darkness he'd spread out had to have alerted Hookwolf's contingent about our existence.



I watched Brian as I walked behind him.  I'd just been paralyzed, about to receive involuntary brain surgery.  Now, in a much different way and for different reasons than before, I was again unable to offer him a hand.  I couldn't even talk to him without being afraid I'd say the wrong thing.



Even compared to being in Bonesaw's clutches, I felt more helpless as ever.





