





I slept, but it was less like parking a car and more like running one into a ditch.  I'd fallen asleep not by any choice on my part, but because I'd ceased to function.  Over the past few days, I'd hit my limits of endurance, only to push past them over and over.



We'd made our escape without incident.  When we'd gotten Brian settled, I'd planned on staying awake and keeping an eye on him, only to drop off to sleep within a minute of sitting down.  I'd tried to push my limits once more and I'd discovered them.



When I woke up again, it was dusk.  I was curled up in a chair with my head on the armrest.  My eyes were sore and itchy, and I wasn't sure why.



We'd settled at Brian's headquarters, because it was close, and there had been the unspoken agreement that it would be better for him to be somewhere he'd be comfortable.



I was still tired, and I kept my head on the chair's arm, clutching the blanket that someone- I suspected Tattletale- had draped over me.  I could see her in the bed in the other corner of the room, lying beside Aisha.  When I'd dozed off, it had been Brian and his sister sitting on the bed.



The blanket's presence unsettled me, and I couldn't put my finger on \emph{why}.  It was thoughtful, \emph{nice}, and the fact that I didn't know who'd done it or that I'd been unconscious and helpless when they'd done it, it shook me from the twilight of near-sleep.



Which meant I was now wide awake when I desperately wanted to get back to sleep, to stop thinking for just a few minutes.  The second I started worrying about things, my shot at a good rest would be gone.  Worrying about things like Dinah, and Cherish's hints that Coil wasn't on the up and up about our deal.  Worries about what that could mean in the long run.  The newest were my anxieties over Grue.



No, I wouldn't be getting to sleep any time soon.  I turned my attention to checking my surroundings, rousing my swarm to check the surrounding streets and rooftops, count the nearby civilians, and get a sense of who was around.



Sundancer was out cold in the bunk beds in another room, and Bitch was sleeping in another bunk, in a heap with Sirius, Bastard and Bentley occupying the open spaces.  Trickster and Ballistic were walking outside, maybe keeping an eye out for trouble.  Genesis was off-site.  She had to be awake for a while to recharge her power, so she'd told us she was going to report to Coil and check on Noelle.  If my bugs were any indication, she wasn't back yet.



Parian had gone her separate way.  She'd had stuff to deal with; her family was dead or surgically altered, their faces changed to make them near identical to some of the most hated individuals in the western hemisphere.  I felt bad about leaving her with the aftermath of that scene, but we'd been prioritizing Brian.



Seems Brian's commentary to me on the morning we'd found out about Dinah, the morning Leviathan came, was ultimately on target.  When the cards were down, we protected and helped the people we care about, and we ignored the greater suffering of the world beyond that.



I shifted restlessly.



My bugs ran into a wall of Brian's darkness in the living room, on the couch.  I could feel it seep through them, tracing their internal organs.  I didn't move them further.  I didn't want to wake him if he was sleeping.



He wasn't.  A hand settled over my bug and covered it.  I felt him scoop up the cockroach and lift it into the air, holding it on the flat of his palm.  The darkness dissipated, and the cockroach heard the bass rumble of his voice.



I made myself rise from the bed.  My ribs didn't hurt anymore, and my burns were gone, but my muscles had kinked up from my sleeping in the fetal position on a piece of furniture meant for sitting.  I stretched as I made my way to the living room.  He was sitting on the couch with his feet firmly on the ground.



``You say something?''  I asked.



``I said you can check on me in person, if you want.''  The words were kind, but the look in his eyes wasn't.



His stare reminded me of Bitch.



``Okay,'' I replied, feeling dumb. I'd come to do that anyways, hadn't I?



And now I didn't know what to do with myself.  I hadn't mentally prepared or planned for this conversation.  I stood there, feeling an impending panic as I tried to think of what to say.



I couldn't ask if he was alright.  That might be the last reminder he wanted, in much the same way that I'd been trying to avoid dwelling on my own anxieties and worries.  Could I approach closer, or would that bother him?  If I left, would I be abandoning him?



``Keep me company?'' he asked.



Gratefully, I approached the couch and sat.  I could see him tense as I jostled the couch.



``Are you hurt?''  I asked, stupidly.



He shook his head, but he didn't offer another explanation.



``Can I ask about the new power, or--''



``Yeah,'' he interrupted.



There was a pause.  I saw him raise his hand and create a slithering mass of darkness around it.



``Feels different,'' he said, ``And I can tell where it is, more.  Slower to create, spreads faster.''



``But the other powers?  I counted at least four.''



``One new ability.''



I nodded.  Didn't want to argue, so I waited.



From the other end of the couch, he raised one hand and pointed it towards my head.  I stayed utterly still as a tendril of darkness snaked through the air, taking its time as it approached.



I stood up, abruptly, and he jumped to his feet in alarm.  I could see his hands clenched, lines standing out in his neck.



An awkward, tense silence reigned, as we stood facing each other.



I waited until he'd relaxed before I spoke.  ``Had a bad time with someone else trying to get into my head, not so long ago.  Um.  Can we- can we just skip the demonstration?  Or make it more blunt?''



``Right.''  It was like a shadow had passed over his face.  He stared hard at the shuttered window at the end of the room.



I sat down,  pulling my knees up in front of me so I could wrap my arms around my legs, and I waited for him to rejoin me.  He'd healed himself, but he hadn't exactly bounced back.  It wouldn't be right to expect him to.  Was this the kind of interaction Tattletale had wanted to avoid, when she'd urged \emph{Aisha} to go to Brian, instead of me?



``I've talked to Tattletale about this.  My power's always had some effect on capes like Shadow Stalker.  Her powers didn't work as effectively in my darkness.''



``Velocity struggled, too.  He was slower, but I wasn't sure if it was because of the increased air resistance or something else.''



``Yeah.  So we think I always had some effect in that department.  That's stronger now.  Affects more powers, according to Tattletale.  She's making an educated guess that this aspect of my power is going to be more effective on capes with a physical power.''



``Right.''



``And when it works, I feel\ldots a circuit?  It's like the darkness comes alive, a cord or wire between me and the people in my darkness, and I can actually see it.  If I focus on it, it gets bright and hot, and I have access to whatever my power's sapping from them.  A fraction of a power, one power at a time.''



``So the healing?''



``Othala.  I was so worried she'd escape my darkness before I finished giving you guys regeneration.  I couldn't just use her power on each of you, because it was only lasting a few seconds after I touched you.''



``And the regeneration was\ldots Crawler?''



He nodded.  I could see that dark look pass over his face.



``And then the duplicate you created would have been Genesis.''



He shook his head.  ``No.''



``No?''



``She wasn't in my darkness, I'm almost positive.  And my power's \emph{weaker }than whatever I'm stealing.  It doesn't make sense that I was able to form myself as fast as I did.  It wasn't like she's described it, either.  Remember, I worked with her when we were dismantling the ABB.''



I nodded.



``It was more like\ldots a forcefield.  Except not.  A hole in reality, and it took something out of me to feed and shape itself.''



I blinked a little in surprise.  If Brian was stealing a share of other people's powers, then-



I blinked again.  My eyes were itchy.



``Damn it,'' I groaned.



He gave me a curious look.  Or at least, that's what I took it for; I was having a hard time reading his expressions.



``Forgot to take my contacts out.  My eyes are going to be sore for a while, and I don't have a spare pair of glasses to wear.''



He nodded.



``Sorry.  So small a problem in the grand scheme of things.''



``You need to be able to see.''



I reached into my utility compartment and got a small case with the spaces for the individual contacts and contact lens solution, then pried my right eye open to pinch the thing out.



A few seconds later, my other contact was out, and I was half blind.  The way the shadows fell over Brian's face, the shadows of his eye sockets made him look like he was wearing sunglasses.  I couldn't see the lines of tension, anger or anxiety.  Whatever it was that'd had him awake, sitting up and staring into space at ten or eleven in the evening.



Maybe I should have left them in.  Risking an eye infection was small potatoes compared to fucking up this interaction.  Except I couldn't put them back in without having to explain why.



\emph{Why was this so hard?}



``You get any sleep?''



He shook his head.



``None at all?''



``Didn't need to.  Didn't want to.  Felt better about keeping an eye out for trouble than about sleeping.''



``Trickster and Ballistic are out there.''



``I know.  I saw them step outside after Rachel came back.''



I smiled a little.  ``Wasn't so long ago that you were getting on my case for not sleeping enough, mandating that I get a certain number of hours before we moved on the Nine.''



He didn't respond, and he didn't move.  I couldn't read his expression.  Had I said the wrong thing?  Should I not have mentioned the Nine?



``Yeah.''  His reply was delayed, almost begrudging.  It didn't sound gentle, or kind, or anything like that.  It was more like I'd expect someone to sound if they were giving up the password to a safe at gunpoint.



``Sorry,'' I said.  I wasn't sure exactly what for, but the apology was genuine.  The smile on my face was gone.



For a minute or two, neither of us said anything.



What had we ever talked about that wasn't about our costumed life?  At first, it had seemed like common sense.  I was new to the cape scene, it was exciting, he was experienced, and he'd wanted to share his knowledge.  We'd talked about our recent jobs, the implications, even jobs we were considering.  I could count on one hand, maybe two, the times we'd done stuff that hadn't been centered around powers and fighting and violence.



Now that I couldn't raise those subjects without reminding him of what had happened earlier, I was lost.



``You shouldn't have come for me.''



``What?''



``Should have left me there.  I was as good as dead.  Throwing away your life and the rest of the team, to try to rescue me?''



``You're not thinking straight.  There's no way I'd leave you behind.''



``Right.  Because you're supposedly in love with me, so you go rushing off to rescue me.''



That stung, more than it should have, and it would've hit me hard anyways.  I couldn't read his expression, so I went by his tone of voice, by the anger, the \emph{bite} in his tone.  The fact that he'd brought it up so casually.



Emma jumped to mind.  She'd been my best friend once, as I was friends with Grue. She'd also flipped on me, turned hostile, and used private thoughts and feelings I'd shared with her to attack me.



I took a deep breath.  ``That wasn't why we came to help you.  And it wasn't just me making the call.''



``Really?  Because I remember you were the one who stopped Ballistic from putting me out of my misery.''



I clenched my fists.  Any resolve I'd had to remain calm was gone.  ``I would have done the same thing for Bitch!  Or Lisa, or Alec, even!  Are you seriously telling me you wish I'd let you die?  You're alive now!  It worked out!''



``Because we got lucky!  Christ, you always do this!''



Using my power, I checked on the others.  One of the dogs had perked its head up at the shouting, but nobody else had roused.  I didn't take \emph{my} eyes off Brian, though.  The look in his eyes was scary.  Angrier than I'd seen him.  I'd unconsciously defaulted to the same defenses I'd used against Bitch: Eye contact, pushing back when pushed.



I deliberately lowered my voice.  ``Always do what?''



``You're smarter than average, so you count on your ability to think up solutions on the fly, you throw yourself into these reckless situations, push and vote for the risky plans because you \emph{know} that's a situation where you thrive, where you offer the most to the group.  Every step of the way, you do it.  Pushing the all-out assault on the Wards at the bank, charging in to fight Lung after taking on Oni Lee, the fundraiser, confronting Purity, attacking Leviathan with zero backup, the attack on the Wards' HQ--''



``Stop,'' I said.  I was getting flashbacks to my conversations with Armsmaster, now.



``You say you're not manipulative, that your undercover operation was pure in motive, but you are.  You throw yourself into those situations solo, or you join in on whatever fucked up plan the others come up with, and you do it because it makes you useful, because you know we'd struggle without you, you're making us \emph{dependent} on you.''



I swallowed past the lump in my throat.  ``That's not- not what I'm doing.  Every step of the way, I had other reasons.  Strategies, or there were people I needed to help--''



``Maybe Bitch was right about you all along.''



``That's not fair.''  \emph{This isn't him.  He's still reeling from what Bonesaw did to him}.



That excuse did little to shake my worries that this was what he \emph{really} thought.  Was this the stuff he was holding back, every day he was with me.



``What's not fair is that I'm the one who's tried to keep things sensible, to keep this group sane, and when push comes to shove, when I go with the majority because things won't go smoothly if I don't, \emph{I'm} the one who gets captured and tortured.  \emph{Your plan}!''



``Don't.''



``Are you going to tell me I'm wrong?''



``It- it wasn't fair.  You're right.  But I don't deserve all of the blame here.  I volunteered to be the person Trickster swapped out.''



``Knowing there was no way you could, with your injury.  So you let me.''  He stared at me with an intensity that I couldn't meet.  I broke eye contact, looking down at my gloved hands, which were clutched together in my lap, fingers tangled.  ``Tell me, Taylor.  If you don't deserve blame, who does?''



\emph{The Nine. Bonesaw.}  But I could hardly say that.  Not after seeing his reaction when I'd casually brought up the Nine before.  However intent he seemed to be on hurting me, I wasn't going to retaliate in kind.



``That's what I thought,'' he said, to my silence.



I looked up at the ceiling, blinking to get the tears out of my eyes.  ``Okay.''



``What?''



``I'll own up to it.  My fault.  The blame is at least partially mine.  Maybe mostly mine.  I've been reckless, and others have suffered for it.  Dinah, my dad, Bitch, the people in my territory.  You.  Maybe I am toxic.  Maybe me and my motivations, my issues, are causing everyone misery.  I can leave the team if you want.  Give me the word, and I'll leave.''



There was a long pause.



``Christ,'' he said.  ``I'm not telling you to leave.  I'm just--''



``You're making it clear I \emph{should}. And you're probably right.''



``I'm frustrated, and I went too far.  That's not what I'm trying to say.''



``Sure sounds like it.''



I stood up and turned away.  I didn't want to see that look in his eyes.



I tugged my armor into position and made sure I had everything I needed.  It wouldn't do to get ambushed and killed as I left.  My modified costume was heavier than my old one had been, and between that and the blanket, and this place's lack of air conditioning, I was sweating.  My hair was stuck to the back of my neck.



He wasn't saying anything.



``I'm going to go.  Half my territory burned to the ground, my people need some attention.  If you decide everyone's better off with me gone, just pass on the word.  I won't make a fuss, I won't say you wanted me gone.  I'll just make an excuse and leave.''



I drew some bugs around my lower face and eyes as a makeshift mask.  My real mask was still in tatters.  I noted that the modifications I'd made were no longer necessary.  I wondered if I would go back to skintight leggings.



It'd be good to get back to my people.  To check on them, and ensure they were okay.  Maybe they'd be better off without me.  If Tattletale or Regent took over the-



``Stop,'' he said, cutting off my train of thought.



Didn't need to hear more of his accusations, his condemnations.  I ignored him and headed for the front door.



``Please.''



His tone had changed.  I stopped walking.



``I've never really said anything like this to anyone,'' he said.  ``But I'm scared.  I'm more powerful now, but I feel more insecure than ever.''



How was I supposed to respond to that?  A part of me wanted to sympathize, to hug him and tell him it was okay.  Another part of me was angry, wanted to slap him, scream at him, because he was still focused on \emph{himself}, \emph{himself,}\emph{himself}, after he'd just attacked me.  I understood why he'd done it, but that didn't make his barbs hurt any less.



``I'm sorry,'' he said.  ``I'm on edge.  I'm spooked.  I can't calm down.  I shouldn't have said what I did.''



``And you can't stop thinking?  I feel like that, all the time, and I have for a while.''



``They had \emph{Aisha}.  So much of what I've done, I've done because I wanted to support her.  Make up for the fact that I wasn't there when she needed it, before.  Only we're putting her in more danger, and she doesn't respect me enough to let me keep her out of danger.''



I turned around.



``And as long as I'm being honest and upfront,'' he said, ``I was thinking about you when I had my trigger event.''



I swallowed.



``I won't lie and say I've suddenly realized I'm in love with you.  I don't really know what I feel, so I can only comment on what I \emph{think}.  I can say I respect you on a lot of levels, even if I can't figure you out.''



``Sure as hell didn't sound like you respected me thirty seconds ago.''



``I \emph{worry} about you.  You throw yourself into these situations like you don't care if you die, like you've got nothing to stick around for except for those people you insist on protecting.  Dinah, the people from your territory.  People you barely know, if at all.  And then you actually make it out okay, so you do it again, only more so.  Riskier stuff.''



I folded my arms.  This was uncomfortably close to what he'd been saying before.



``I start thinking about how I'm supposed to protect you, get you to stop, get you to focus on a goal that's actually attainable, because you're so capable that you could be amazing if you stopped acting suicidal.  Then I get pissed at myself and I get pissed at \emph{you}, because I can't figure you out, and you move forward so fast that I can't keep up.  I let my guard drop for one evening to focus on other things, and then I find out you'd gotten in a fight with \emph{Mannequin}.''



``It's not your job to look after me.  If you want to get on my case because I'm putting you and the others at risk, that's fine.  It's your right to yell at me for that.  But don't make me feel bad because you can't be the macho guy, protecting me.''



``That's not--'' he stopped.  ``No.  I'm trying to say I think about you more than I should.''



I looked away.  I might have asked whether he thought about me more than he should because he cared, or because I was a fuck up.  I wasn't sure I wanted to hear the answer, either way.



``Stay?  When I asked you to keep me company, I was being genuine.  Rather not be alone with my thoughts.''



I sighed.  ``I could do with some tea.  I could make you some coffee if you wanted.''



He shook his head.  ``Jumpy enough already.''



``I'll be right back.''



I headed into the kitchen, put a kettle on and began digging around for teabags.  It wasn't easy, when I was half-blind.



Once I had the teabags and a mug set, I got my cell phone out.



``Cranston here,'' the woman on the end of the line replied.  ``What can I do for you, Skitter?''



Cranston was the woman Coil had assigned to me, as he'd assigned employees to the others, so he wasn't personally dealing with each of us when he had other things to focus on.



``Need glasses.  Coil has the prescription on file from when he got me my contacts.''



``I'll have them for you by morning.  Anything else?''



``No- wait.  Yeah.  Can you pass on a message to the PHQ?''



``Coil has contact information.  Hookwolf's contingent exchanged contact details with the other teams, including the PHQ.''



``No.  I mean, without going through Coil's channels.  I need to give them a message from \emph{me}.''



``That can be arranged.  I have a pen and paper, if you'd like me to take dictation.''



``Tell them Burnscar's dead and Bonesaw's missing a pair of hands for at least a little while.  Four and a half members left.  If they were being honest about waiting for the right moment to strike, this is probably a good one.''



``Mm hmm.''



``We can give them the location of the Nine if they're interested.''



``Should I give them your contact information?''



``They have enough tinkers that I'd be worried about them tracking me down.  No.  If they want to get in touch, I'll leave it to them to figure it out.  Not going out of my way.''



``Alright.''



``And one last thing.  Tell them `thanks for the help'.''



``I'll get the message to them promptly.''



I hung up.



I returned to Brian with a mug of tea for myself and a glass of water for him.  The television was on, and he sat in the middle of the couch.  He patted at one cushion.  With the way he was positioned, there was no way for me to sit a distance from him.



At the same time, when I did sit, he didn't reach out to touch me, to put a hand on my shoulder, or any of that.  We watched terrible late night TV with the volume so low we could barely hear it, not talking, not making body contact, barely even looking at each other.



He'd confessed feelings for me, after a fashion; I had a special place in his thoughts, even if he didn't know what that meant, exactly.  We were sharing personal parts of ourselves we'd never let others see.  We even cared about each other.



I just hadn't wanted it like this.





