





``Sam!  Sam!''  Celia's voice was grating and nasal.



``I'm coming!''  The heavyset man grumbled, as he made his way into the living room.  Celia sat on the floor between the couch and the coffee table.  The white of her t-shirt and panties was a stark contrast to her dark skin.  Sam leered at the woman.  She was good-looking for her age, slim, though her breasts sagged behind her shirt without the benefit of a bra.



``You said you were five minutes ago, asswipe.  Takes you five minutes to find your wallet?''



``Needed to piss.  Your fatass friend was in your bathroom, so I pissed in your sink.''



Celia kicked under the coffee table to strike his shin.



Sam just smiled and stepped back.  ``Kidding.  I went off the fire escape.''



``That's not any better!''



``It's all water and shit down there.  Any place that doesn't smell like hot garbage smells like a toilet.  Here.  Stop bitching.''  He threw a plastic movie rental card at her.



She cut open a plastic wrapped block of powder and shook a small amount of the powder onto the coffee table.  She used the laminated card to cut it into lines, a set on each side of the table, with none in front of her.



``You're not having any?''



``I told you.  I'm pregnant.''



``You're too old to be pregnant,'' Sam commented.  She kicked him again.



``Not that old!''



Jennifer emerged from the washroom and stopped in the doorway, staring at the scene.



``I didn't think you'd actually use any of the stuff.''



``Jen, hon,'' Celia said, ``We've got enough to go around.  Even if we only sold half, we'd be made in the shade for five or ten years.''



``And you just took it?''



``Leaders of the Merchants got killed, everyone else decided to run off with what they could carry of the stockpiles.  Sam and I decided to play it \emph{smart}.  Sam got his truck, and I guarded the stash from the other assholes.  Paid off.''



``I\ldots what is it?''



``Little bit of everything.  Come, sit.  Try some.''



``What \emph{is} it?''



Sam seated himself at the table, by one set of the lines of powder.  He picked up a pinch and put it on his tongue.  ``H.''



``No way,'' Jennifer said.  She dropped into one of the felt-covered chairs at the far end of the room.



Aisha had to hop out of the way so she didn't get sat on.  She watched the dialogue between her mother, her mother's boyfriend of the week and her mother's new friend with a dispassionate expression.  Seeing this scene, she didn't really \emph{feel} much.  A little disappointment.  Embarrassment.  Disgust.



No, it was less this scene and more the discovery that her mother was pregnant that nailed her in the gut with a profound kind of sadness.



The first place her mind went, before joy at the idea of having a brother or sister, before anger at her mom for letting it happen and not using protection, was hope.



``Sam, do you have any papers?''



``Rolling papers?  I thought you were going clean.''



``It's just weed.  I need to have \emph{something}.''



``Isn't that bad for the kid-in-progress?''



``It's \emph{weed}, dumbass.  Nothing they tell you about it is true.  Kid isn't going to wind up addicted from birth or anything, 'cause it's not addictive.  Right?''



``Sure,'' he reached into his back pocket and slipped a packet to her, along with a dime bag.



Aisha bit her lip.  Maybe hope was the wrong word, because she didn't really feel anything on the subject.  But she knew it would probably be better if her mom miscarried and the kid was spared this shit.



How much of Aisha's problems were because of her mom's lack of self-control and how many others were because of this environment?  She'd grown up with a mom who'd never mentally or emotionally aged past fourteen or fifteen.  A new man in the house every week or two, with his own idea of how things should work, Celia generally content to let him run things however he wanted.



Aisha tried not to think about the men.  It was like having a broken arm; so long as she didn't move it, so long as she didn't think about it, it was okay, a dull throb in the back of her mind.  Something she could ignore.  But even a stray thought could remind her that the arm was broken, and then it sometimes took days before she could get out of that head space.  There was no distraction that worked, because the fact that she was consciously \emph{looking} for a distraction only reminded her of what she was trying to distract herself from.



Of course, there was no way to avoid the countless reminders in everyday life that would remind her of Guy, or Bridge, or Darren, or Lonnie.  Thinking about a broken arm was one such reminder.



Being ignored by her teammates and told to go to her room and play along for everyone else's sake was another.  How many afternoons had she come home from school, only for her mom or one of her mom's boyfriends to shoo her off or bribe her to leave the apartment for a bit?



Pissed her off.  She didn't need that from her brother, too.



``Come on, Jennifer,'' Celia urged her friend.  She took a long draw from the spliff she held in her fingers. ``Oh fuck!  Sam, you jackass!  This isn't just weed, is it?''



``Thought it was.''



``There's a kick to it.  Amp or something.''  Celia took another puff.  ``Amp.  Hey, Jen, join in. Have some of what Sam's having.''



``But H is fucking scary,'' Jen protested.



``So you hear.  But \emph{why }is it scary?''



``It's addictive.''



Aisha tuned out the sound of her mother and Sam cajoling the woman and walked over to the table.  Her mom didn't notice her.  Nobody ever noticed her, and they noticed even less ever since she'd gotten her power.  It was like a dark joke, a grim comedy.  Just when she'd started to figure things out, grow up and catch people's eye, the world went to hell and she got her powers.  Now she became invisible if she lost her concentration.



Not that it was invisibility, really.  It was memories.  People forgot her as soon as they saw her, to the point that they didn't register her presence.  She could feel it, her power rolling over her skin, jabbing outward, invisible to sight, touch and anything else, making contact with the people around her and pushing those memories away.



And like her metaphor comparing her memories to a broken arm, her power seemed to respond to the attention of her subjects; the harder they tried to remember and focus on her, the faster she slipped through their minds.



The metaphor applied in another way, too.  Her power operated on its own, doing its thing, and if she very casually noted what it was doing, without pushing it forward or holding it back, she could feel it doing something else.  As if it was ready to push away memories that didn't relate to \emph{her}, exactly.  It never did.  Any time it built up enough that it came close to doing anything, she noticed, and it retreated like a turtle pulling its head into its shell.



Frustrating.  Her power didn't do anything because she wanted it to.  It worked only if she \emph{surrendered} to it, let it act on its own.  Pushing it to work harder had the opposite effect.



How easy would it be to just carry this stuff away?  She could hand it to Coil for some brownie points, and he could decide what to distribute.  It would be out of her mother's hands, and money would become a limiter on her mother's habit.  If the drugs weren't around, maybe Sam would leave.



Maybe, if Aisha got rid of the drugs, her mom would have an excuse to get things back on track, somehow.  The city was paying people who joined the clean-up crews.  Three square meals, simple and bland but they gave the essential nutrients, and they gave you twenty dollars for nine hours of work.  Fuck around or slack off, and they just kicked you off the crew for the day, no pay.



Idle hopes.  Aisha had spent long years wishing her mom could pull it together, dating back to just after the divorce, when a bad day was still better than most good days were now.  Or maybe that was nostalgia and a child's eye view.



No.  If she got rid of the drugs, it was more likely that someone would erupt in anger.  Sam or her mom, getting violent, verbally or otherwise.  It would do more harm than good.



She sat down on the coffee table, directly opposite her mother.  Reaching forward, she plucked the spliff from her mother's lips and dropped it, grinding it under her toes.



Her mother blinked a few times, then reached for her rolling papers.



Aisha used her hand to cover the papers and whispered, ``No.''



Again, the dazed blinking.  Her mother asked, ``Sam?  Got any more papers?''



``I just gave you a full package.''



``The hell?  Maybe that hit me harder than I thought,'' Aisha's mother giggled.



Aisha stared her mother in the eyes.  She didn't deactivate her power.  ``Mom.  You gotta stop.''



``Where are the rest of the papers, Sam?'' her mom asked, oblivious.



``Kitchen.''



``But I don't want to get up.  I'm comfy,'' Celia whined.



``You keep going down this road, your kid is going to be born without a face or something,'' Aisha said, her voice quiet.  ``You know how hard school was for me?  Even as far back as kindergarten, I couldn't sit still.  Teacher tells me three things, and by the time they've gotten to the third, I've forgotten the first.  And Brian doesn't have any of that.''



``Go get some papers, Sam.  Sam McSamsam.  Sammy-sam.  Samster--''



``I don't want to get up any more than you do,'' Sam growled.  ``You're not one of the talkative ones, are you?  I like it quiet.''



``Mom,'' Aisha said, as if she could get her mom's attention.  Ironically enough, she knew that if she deactivated her power, she'd have even \emph{less} chance of talking to her mom.  It wasn't just the horned mask and the black costume.  She'd never had anyone just sit down and listen to her.  Dad ignored her, mom was self-centered and Brian was too focused on what needed to be \emph{done} that he ignored everything else.



``Mom.  You're going to have some fucked up kid, and then you're going to die of an OD before it's even grown up.  It's not fair that you leave some kid that's more retarded than me, or some deformed freak for Brian to take care of.  Not fair on him, and it's not fair on the kid to make them put up with the dick, either.''



``Fine,'' her mother said, standing.  ``I'll get the papers myself.''



Aisha sighed.  Was it cowardice that kept her from confronting her mother, or the knowledge backed by years of experience that it wouldn't make a difference?



Maybe, if everything with the Nine worked out and Coil got control of the city, maybe she could get her mom some help, or report her to the police.



But not now, not when things were like this, when she had to prove she deserved her place in the group.



Abandoning her mother to a noisy search of the kitchen, Aisha headed into her old room.



Her room smelled like sex, and faintly of urine.  Her mom had apparently had a party since Aisha had left.



Holding her breath, she opened her closet door.  She pushed past the clothes she'd stolen, shoplifted and bought, and past the old clothes she couldn't or wouldn't wear anymore.  Her closet was in layers, and each layer held clothes and trinkets from a different era.



Her girl guide stuff was in the very back, too wrinkled by years to wear.  Her dad had pushed her into that.  He'd wanted her to have structure.  After a year and a half, even he had pulled her out.  A bad fit.  She didn't have the personality type for it.



Around the girl guide stuff, she found a small tape recorder and an old pair of binoculars.  After finding an old backpack that had never been emptied of the school supplies, she found some notebooks that had only been filled in about a third of the way.  She tore out those pages and tucked the notebooks under one arm.



Everything went into a compact black handbag, along with her taser and knives.



Small things.  Nothing she couldn't have bought in a well stocked convenience store, maybe.  But she would operate best if she was relaxed, and having some personal items made her feel better.



That only left the problem of finding them.



They'd attacked the Merchants, and observing her mom had given her the chance to find out where.  It was a starting point.



\sectionbreak



It was worse than she'd expected.  She ducked under the police tape and pushed one officer out of her way as she stepped into the area.  Police cars and PRT vans had formed a broad perimeter, with police tape strung between them.  She momentarily wondered why they didn't have the wooden barricades.  It was flimsy as security went.



It was drizzling, and the small amounts of rain did little to clean the streets of the blood that spattered it.  Water soaked into the white and brown sheets that had been draped over the bodies that still waited for someone to clean them up.  The brown, she realized, was dried blood.



Aisha picked her way through the fallen.  The worst of the carnage was at the edges, as if some invisible line had been drawn that nobody was permitted to cross, and in the center, where the masses of people had gathered before being murdered together.



She'd hoped for a lead.  A piece of evidence, or an overheard tidbit of information from the cops.



No such luck.



There was an overabundance of evidence.  By the time the cops processed everything here and managed to identify the bodies, the leaves would be falling off the trees and the Nine would be long gone, one way or another.  The cops weren't talking, either.  They were working silently, or the things they were saying weren't interesting.  Catching the Nine wasn't their job.  If they found something worthwhile, they would pass it on to the local capes, probably.



No.  If there was something to be found, it wouldn't be here.  She headed to the edge of the scene, where the police cars had all stopped.  There were still spots and spatters of blood here and there, and bloody footprints, but not much.  She walked around the police and the cars to check each set out.  In every case, it seemed, the bloodied victims had either fallen where they lay or disappeared.  Ambulances?



Having checked the area, she moved further down the street to see the next closed-off alleyway.  The same thing.  A few more bloody footprints, but nothing beyond that.



The third blockade offered something.  There was a spot where the blood was thicker, which didn't match up with the other spaces.  The trail extended further than it did elsewhere.



Looking around, she spotted a smear of blood on the side of a building, three stories up.



Okay.  So maybe they'd gone this way.



The trail of breadcrumbs that the blood provided were slowly being eroded or masked by the light rain.  The water raised the oils from the cracks in the road, giving the ground a rainbow sheen.



The signs of blood faded too soon, and Aisha could only guess whether she had taken the wrong road, gone too far or if the rain had cleared it away.  She might have given up right then, but she saw a group of men standing outside of an apartment building.



It was only when she got close that she saw the badge clipped to the front of one of their jackets.  A detective.  There was blood on the door that led into the apartment lobby.



The elevator wouldn't be working.  She headed for the stairwell, only to find more blood.  It was as though a body had been dragged.



Going forward was a stupid idea, she knew.  Brian and Skitter had gone into way too much fucking depth about the risks.   Still, that hadn't stopped her before.



She got her taser and knife from her bag and made her way upstairs.



Third floor up, blood on the door leading into the hall.  More blood trailing down the hallway, stopping at one apartment.



She double checked that her power was active and pushed her way inside.



Only a few of the Nine were present.  Crawler slept with his ponderous head on paws that were crossed over one another, his back rising and falling with each deep breath.  He was large enough that the highest part of his back rose nearly to the ceiling with each breath he drew in through his nostrils.  Only half of the eyes on his body were closed, covered with thick, dark gray lids.



Shatterbird and Burnscar were on the couch, Burnscar stretched out with her head on the armrest, her feet propped up on Shatterbird's lap.  She held a graphic novel on her stomach with one hand and created flames in the other, shaping them to match the people she saw as she flicked from page to page.  Shatterbird was sitting upright, a novel in her hands.



Bonesaw stood over the dining room table, with a mechanical spider-thing on the opposite side of the table, assisting her.  A young man was on the table itself, his wrists and ankles tied down.  His torso was open from collar-bone to crotch, his ribs splayed apart.  Bonesaw and her mechanical spider were elbow deep in the contents of his torso.



\emph{The spiders}.



Aisha moved quickly aside as a spider moved from the kitchen, past her and to the table.  Whatever cameras or artificial intelligence it used, it didn't seem to notice her.  It handed Bonesaw a diet cola that the little girl opened with bloody fingers and drank.



With a little more confidence, Aisha moved further inside, giving a wide berth to Crawler and Burnscar's foot-high images of flame.



Holding her weapons, Aisha stood next to Shatterbird, at one end of the couch.



Aisha had never killed anyone, but here she was, holding a lethal weapon.  She could slice Shatterbird's throat and they wouldn't even realize she was there.



They would, she suspected, realize that Shatterbird was dead or dying.  There was a fifty-fifty chance, anyways, that it would force them out of whatever effect her powers had on their brains.  It had happened to her before.



Except that Shatterbird would kill her in her last moments, using the glass that had been swept to the corners of the room, or one of the others would.  Burnscar or Crawler could deal a hell of a lot of damage, even if they didn't know who they were attacking.



Slowly, she walked over to Bonesaw, navigating around the drones.  Could she kill the kid?



On the one hand, Bonesaw was the one who kept the other members going.  Removing her would take a lot of problems off the board.  She could finish off Bonesaw and run for cover in the kitchen, out of Burnscar and Shatterbird's line of fire.  From there, it was only steps to the front door and safety.



On the other hand, it was still murder, and it was a \emph{kid}.  A kid that had a hundred kills under her belt.



A squeaking sound distracted her from her thoughts.  It was like air being let out of a balloon, but in shorter spurts.  Bonesaw?  No, the girl wasn't making any noise.  The mechanical spider?  No.  Not the spider either.



Stepping as close to Bonesaw and the spider as she dared, Aisha investigated the sounds.  Where were they coming from?



Bonesaw smiled, ``You're going to have to speak up if you want me to hear you, Jonathan.''



\emph{Jonathan?}



Aisha looked down at the body, and realized the heart was beating inside Bonesaw's hands.  The man's eyes were moving, and his lips moved as he struggled and failed to make words come up through his windpipe.



The surge of horror and disgust gave Aisha the strength to cast aside her doubts.



``Sorry kid,'' she said.



She plunged the knife into Bonesaw's bare throat.



Bonesaw screamed, shrill and loud, which caught Aisha off guard.  With a knife in her throat, the girl was screaming?



Reacting more on instinct than wit, Aisha pulled the knife out and then slashed it horizontally across Bonesaw's throat.



She'd expected a spray of blood or gurgling.  Neither happened.  Bonesaw screamed again.



So she pulled the knife free and stabbed Bonesaw in one eye.  The blade scraped against the bone of Bonesaw's eye socket.



Flame erupted and pieces of glass came to life around Aisha.  She backed away quickly as a wall of flame rolled over Jonathan on the table and divided her from Bonesaw.  There was a rumble and the sound of falling furniture as Crawler stood.



``Ow, ow, ow, ow!''  Bonesaw shrieked.  ``It hurts!''



\emph{Why isn't she dead?}



Aisha yanked the knife out and then gripped her taser.



``Is it Jack?'' Burnscar asked, looking around, then turning to the window, ``What the hell?''



``It's not Jack,'' Bonesaw said.  She snapped her fingers, and the mechanical spider leaped on top of her, beginning to suture the wounds in her neck.  ``I gave Jack the same safeguards I gave us, he would have succeeded if he tried it.''



Shatterbird scowled.  ``Then who or what was that?  Crawler, do you know?''



Aisha backed toward the front door.  She stopped as Crawler appeared in the doorway that led from the kitchen to the front hall, looking through to see his teammates on the far end.  His voice was a mangled mess of sounds that only barely approximated anything like speech.  ``I don't smell anyone.''



\emph{Smells can't find me, then, }Aisha thought.  Still, she didn't have her escape route.



``Torch the apartment and make a break for it?'' Burnscar asked.  ``We can meet up as a group later.''



``No.  Cherish has a hard time tracking Mannequin, and he won't know how to find us,'' Shatterbird said.



``I'm okay,'' Bonesaw piped up.  She held one hand to her eye socket, which had trails of smoke rising from it.  ``You don't need to worry.  I can put my throat back together easy, after I get my kit out to check the sheaths for my vitals to make sure there's no abrasions, and I've got spare eyes.  I could go with green eyes.  Or one green and one blue, or if I alter them, I could have-''



``Quiet,'' Shatterbird cut in.  ``It's less about you being hurt and more about the fact that someone had the \emph{audacity} to attack us here.  Burnscar, put out those fires.  We don't want attention.''



The wall of flame shrunk and faded away.



``Really hope you don't have another way of sensing me, big guy,'' Aisha said to Crawler, ducking between his legs and stepping towards the door.  ``I'm gonna make my exit now.''



None of the Nine reacted as she shut the door behind her.



Lesson learned.  The more `vulnerable' members of the Nine weren't as vulnerable as they looked.  Sheaths, Bonesaw had said?



Stepping into the lobby, she stopped in her tracks.



One of the detectives who'd been standing by the door was dead, his throat slit.  He laid in the center of the lobby.  Two more blood trails ran to the side of the lobby opposite the stairs.



Manager's office?



Her weapon drawn, she reached for the doorknob, and collided with Jack as he strode out of the office.



``What's wrong?'' Cherish asked.



Aisha backed away.



``Nothing,'' Jack said.  ``You grab the last body and then find a mop.''



``Me?''



``I think I've been \emph{exceedingly} generous, giving you a second chance.  You can repay me by doing the heavy lifting.''



``Ever the gentleman.''



``Go on, now.  I'll wait here.''



Aisha watched as Cherish walked past her, grabbed the heavyset detective and began dragging him inch by inch toward the office.



She only remembered one other time when her heart had pounded this hard.  It had been when the fledgling Merchants had attacked her and her father.  It was another chance.  While they were separated, she could go after one.  But which?



She held the taser and the knife, adjusting her grip so she was secure.



Jack was the key figure.  Aisha knew she could attack him, knew she maybe \emph{should}, but would she succeed any more than she did against Bonesaw?  Cherish might be able to lash out with some kind of blind fire, affecting the emotions of everyone nearby.



No.  Cherish was the newest member, wasn't she?  There were better odds that Cherish didn't have the protections that Jack and the others did.



Exhaling slowly, Aisha followed behind Cherish as the girl tugged the body into the other room.  She stepped inside and shut the door.



``Put the weapon away,'' Cherish said, her voice quiet.



Aisha gulped, realizing the trap she'd just stepped into.  ``You can hear me?''



A second passed, and there was no response.



``Put it away, or I'm going to leave you quivering in a corner, shitting your pants.''



``You \emph{can't} hear me.''  Aisha gripped her weapon and stepped closer.



Cherish whirled around, her eyes flitting right and left, searching for Aisha.  ``I'll scream.  He'll come in here, and a couple swings of his knife, he can cut you down, invisible or no.''



``It's not invisibility,'' Imp said, uselessly.



``Put your weapon away,'' Cherish said, her voice quiet and carefully measured, ``We only have a few seconds before Jack gets suspicious.  Listen.  I want to strike a deal.''

