





\emph{It's like the world's gone mad, and I'm the only sane person left}.



Director Emily Piggot finished the last of her coffee and paused to survey the enormity of the task that lay ahead of her.  The scale of it could be measured in paperwork.  Piles of it.  Sometimes two feet high, the stacks of paper were arranged in rows and columns on every available surface, including the top of her coffee maker and the floor around her desk.  There were stacks of stapled pages, each topped with a weight to protect it from the gusts and breezes that flowed through the open window frames.



She couldn't help but notice the way that the pages at the bottom of the pile were neatly organized, tidy, everything in line.  The newer pages, the ones at the top, were the sloppy ones.  Pages were slightly out of alignment, some dog-eared or stained.



The same progression could be measured in the print.  The older pages were typed, printed as forms with everything in its place.  Abruptly, it all shifted to handwriting.  Shatterbird's destruction of everything glass and everything with a silicon-based chip inside.  Computer screens and computers.  The handwriting, too, grew less tidy as the rise of the piles marked the passage of time.  On occasion, it would improve for a day or two, when her captains and sergeants complained about illegible handwriting, but it inevitably slipped back into disarray.



\emph{A strong metaphor}, Emily Piggot thought.  Every part of it said something about the current circumstances.



The shift from uniform typed words to countless styles of handwriting, it said something about the innumerable voices, the break down of the cohesive, ordered whole.  What resulted were hundreds, thousands of self-interested voices.  One in five condemned her, two in five pleaded with her for assistance in some form, and the remainder simply expected her to perform her duties as a cog in the machine.



She looked over the sheer volumes of paper around her office.  The PRT handled cases where parahumans were involved, and these days, it seemed like everything and everyone was touched in some way by the heroes, villains and monsters of Brockton Bay.  Every time the other precincts had the slightest excuse, they would claim that it was the PRT's responsibility.  If they had no excuse at all, they would claim it a joint responsibility.  Until she read over the cases in question and either signed off on them or refused them, the job was in her hands.  As far as the ones passing the buck were concerned, it was out of their hands.



The first real intrusion on the average citizen's life had been the bombings instigated by the ABB.  Frightening, but it had been easy for the average person to believe they wouldn't be one of the victims, to shrug it off as the same background noise of heroes and villains that they'd experienced for much of their lives.  Now, between Leviathan, Shatterbird, the fighting and the formation of territories, everyone had reason to worry and give serious thought to who they needed to support and how they were going to protect themselves.



Just as the parahumans had invaded the lives of those in the city, the paperwork seemed to dominate Emily's life.  It crept onto the walls, onto bulletin boards and whiteboards.  Notes on the local players, timelines, messages and maps.



Insurmountable.  Too much work for one woman to handle.  She delegated where she could, but too much of the responsibility was hers and hers alone.  The humans outnumbered parahumans by eight-thousand to one, give or take, in urban areas.  Outside of the more densely populated areas, it dropped to a more manageable one to twenty-six-thousand ratio.  But here in Brockton Bay, many had evacuated.  Few places in the world, if any, sported the imbalanced proportion that Brockton Bay now featured.  What was it now?  One parahuman to every two thousand people?  One parahuman to every five hundred people?  Each parahuman represented their respective interests.  She represented everyone else's.  The people without powers.



The whole nation was watching.  People across America ate their TV dinners while they watched the news, seeing footage of the slaughters in downtown Brockton Bay, white sheets draped over \emph{piles} of bodies.  The before and after shots of areas devastated by Shatterbird.  Flooded streets.  Fundraising efforts were launched, many succeeding, while yet others leveraged the situation to cheat the sympathetic out of money.  The world waited to see if Brockton Bay would become another Switzerland, another Japan, another region that simply couldn't recover.  Ground lost to the Endbringers in their relentless campaign of attrition against humanity.



So very few of them knew it, but they were counting on \emph{her}.



She heaved herself out of her chair and made her way to the coffee machine to refill her mug.



``Director?''



She turned to see Kid Win standing in the doorway.  He looked intimidated.



``Yes?''



He raised the laptop he carried in his hands.  ``The guys in CS asked me to bring this to you.''



She shook her head, refusing the offer, ``For now, every computer that comes in is supposed to be used for setting up the consoles and communications.''



``They're done.  Or almost done, for communications.  They expect to be up and running in two hours, but they have all the computers they need.''



``Good.  Access to the central database is up?''



``Everything except the highest security feeds.''



\emph{Disappointing.  }``I'll make do, I suppose.  Thank you.''



Kid Win seemed almost relieved to hand her the laptop.  It meant he could get out of her presence sooner.  He was turning to leave the instant the laptop was out of his hands.



``Wait.''



She could see his shoulders drop, slightly, in the same way a dog's tail drooped when ashamed or expecting reprimand.  Emily Piggot wasn't good with kids, or even young adults.  She knew it.  Outside of the time she had played with dolls as a small child, she'd never entertained the notion of being a mother.  She didn't even \emph{like} kids.  It was the rare youth that she actually respected, now, and those few tended to be the ones who saw her firm leadership and respected \emph{her}, first.  Now she was in charge of some of the most powerful children in the city.



``The next patrol shift is in\ldots''  She turned to find the clock, ``Twenty minutes?''



``Twenty minutes, yeah.  Vista, with Clockblocker babysitting.  Weld and Flechette are out right now, patrolling separately.''



``Postpone the next patrol, and tell Weld and Flechette to take it easy, but to be ready to report at a moment's notice.  With the consoles up, we'll be ready to act.  Pass on word to Miss Militia as well.  I believe she's taking the next patrol shift.''



``Yes ma'am.''



The laptop would do little to help in her war against the paperwork until she had access to a printer.  PRT divisions and precincts in neighboring cities were all too willing to send along staff and officers to assist, but her firm requests for the fundamentals -for computers, printers, satellite hookups, electricians and IT teams- were ignored all too often.



She cleared space on her desk and started up the laptop.  It would be good to have access to the files on the locals and `guests' alike.  She would handle the paperwork better after a moment's break, while she focused on other things that needed doing.  She was barely registering the words, at this point.



This would be a battle won with preparation, and for that, she needed \emph{information}.



It took her a moment to adjust to the smaller keyboard.  She entered her passwords, and answered the personal questions that Dragon's subsystem posed to her.\emph{  Why is your nephew named Gavin?  Your favorite color?  }Irritating- she didn't even know her favorite color, but the algorithms had figured it out before she did.  All information divined from the countless pieces of data about her that were in official emails, photographs and surveillance footage from the PRT buildings.  It was with a moment of trepidation that she typed in \emph{For Gawain, knight of the round table.  Silver.}



The fact that Dragon's system could divine these details, as always, unnerved her.  This time, in light of recent events, it unsettled her all the more.



She typed in the words `Slaughterhouse Nine' and watched as information began appearing in lists.  News items, sorted by relevance and date, profiles, records.  Lists of names.  Casualty reports.



Emily clicked through the records.  Sorting as a timeline, she found the entry muddled with Armsmaster's simulation records on the fighting abilities of the Nine.  He'd been preparing to fight them.  A double-check of the modification dates showed he'd seen the entries recently.



So when he'd escaped, he'd done it with the intent of fighting the Nine.  She'd suspected as much.



She refined the search to remove the simulations from the results and found video footage.



A video of Winter, an ex-member of the Nine, engaging in a protracted siege against no less than twenty members of the Protectorate.  She'd been killed by one of her teammates.



A sighting of Crawler, shortly after he had joined the Nine.  He'd been more humanoid, then.  Still large.



Another member of the Nine from yesteryear, Chuckles, attacking a police station.  No use to her, beyond serving as a testament to what might happen if she consolidated too many forces in one place.



She found a file listed as `Case 01'.  She clicked it.



``\emph{We've got her cornered?}'' the person in the video spoke.  Hearing the voice, noting the camera image of an apartment was mounted on a helmet, Emily Piggot knew who it was.  She knew the video well enough.



``\emph{Think so},'' a man replied.  The camera focused on Legend, then swung over to Alexandria, and finally Eidolon.  ``\emph{We've got teams covering the drainage and plumbing below the building, and the entire place is surrounded.}''



``\emph{She hasn't tried to leave}?'' the face behind the camera asked.  ``\emph{Why not?}''



Legend couldn't maintain eye contact.  ``\emph{She has a victim.}''



Alexandria spoke up, ``\emph{You had better be fucking kidding me, or I swear-}''



``\emph{Stop, Alexandria.  It was the only way to guarantee she'd stay put.  If we moved too soon, she'd run, and it would be a matter of time before she racked up a body count elsewhere.}''



``\emph{Then let's move,}'' she responded, ``\emph{The sooner the better.}''



``\emph{We're trying an experimental measure.  It's meant to contain, not kill.  Drive her towards main street.  We have more trucks over there.}''



Emily turned off the sound as the four charged into action.  She didn't want to hear it, but she felt compelled to keep watching.  A matter of respect.



It was Siberian.  One of the first direct confrontations, more than a decade ago.  It hadn't gone well.



The Protectorate had been smaller, then.  The lead group had consisted of four members.  Legend, Alexandria, Eidolon and Hero.  Hero had been the first tinker to take the spotlight, so early to the game that he could get away with taking a name that basic and iconic.  He'd sported golden armor, a jetpack, and a tool for every occasion.  His career had been cut short when Siberian tore him limb from limb in a sudden frenzy of blood and savagery.  He'd been scooped up by Eidolon, who tried to heal him, who continued to hold the man as he joined in the ensuing conflict.



Director Piggot had seen the film before.  Several times.  It was the screams that haunted her.  Even with the sound off, she could have put it all together from the sounds that were engraved in her memory, right down to the cadence, the pitch.  Seeing a teammate die so unexpectedly, so suddenly.  The noises of panic as some of the strongest capes in the United States realized there was nothing they could do, adjusting their tactics to try to save people, staying one step ahead of Siberian to minimize the damage she did as she waded through any defense they erected, tossing the PRT trucks -modified fire trucks, then- as though they were as light and aerodynamic as throwing knives.



Invincible Alexandria was struck a glancing blow and had one eye socket shattered, the eye coming free in the midst of that bloody ruin.  Eidolon had healed her, after, but the scar was still there.  Alexandria now wore a helmet whenever she was out in costume.



After that telling blow, Legend's voice would be ordering the containment foam.  Not so much to bind Siberian as to hide the wounded Alexandria from the feral lunatic.



With the sound muted, Piggot would not have to hear Legend crying out over what he had believed was the death of two teammates.  It had always made her feel guilty to hear it, as if she were intruding, seeing someone mighty at a moment in their life when they were stripped emotionally bare.



And of course, Siberian had escaped.  Slipped past countless PRT officers and a dozen superheroes in the chaos.  Nothing in the footage gave a clue as to how.



A shadow passed over her desk.  Turning, she saw a silhouette of a flying man against the light of the sun.



Like so many parahumans, he lapsed into intrusiveness and a self-centered mindset.  Well, she wouldn't blame him for being emotional in regards to this.



She composed herself and spoke, ``If you'd like to enter my office through the front door, Legend, we can talk there.''



Silently, he disappeared around the side of the building.  She couldn't see through the wall, but she heard the commotion as he flew in through the window.  He stepped into her office with the fluid grace one had when they could use their ability to fly to carry their weight.  Blue and white costume, boots and gloves.  Veteran member and leader of the Protectorate, his lasers carried as much firepower as a battalion of tanks.  She had to remind herself that she technically outranked him.



``Siberian?'' he asked.



``I'm reading up on our opposition.''  She wouldn't apologize, but she couldn't keep the sympathy from her face.



``I flew up to check if you were in your office, and I saw the video.  My fault for seeing what I did.  It wasn't a good day.''



She nodded curtly.  It hadn't been.  One could even suggest it was when things started to go bad.  The loss of Hero, the first time a truly dangerous villain made an appearance.  ``What did you want to see me for?''



``A note delivered for you at the front door.  We gave it a high priority.''



``You're taking the standard precautions?''



He nodded.  ``It's already on its way to the lab.''



``Join me?''  She lifted herself out of the chair, keenly aware of the differences in her and Legend: parahuman and human, male and female, lean muscle and eighty pounds of extra weight, tall and average in height.



``Of course.''



They walked past the reams of public servants, government employees and Piggot's own people.  Emily knew she was not the only one overburdened with work, not the only one sweating, trying and failing to keep cool.  The rest of her people were staying awake with the benefits of coffee more than anything else.



She couldn't turn away everyone that volunteered or was sent to Brockton Bay to assist her PRT division, but there were too many.  Space was at a premium, and there were too few places where she could establish secure offices, where buildings didn't threaten to fall down and where assistance was actively needed.  Still, she'd sent people away when she could.



``How's the family?'' She asked.  ``You adopted, if I remember right?''



``We did.  Arthur was worried that a surrogate parent would give birth to a parahuman, and if that happened, he'd be out of the loop.''



``The odds are still high, even with an adopted child.  It's likely more to do with exposure to parahumans at formative ages than genetics.''



``I know.  Arthur knows, but I don't think he believes it.''



``Or he doesn't want to believe,'' Emily said.



Legend nodded.



``He knew the price of admission,'' she said.



Legend smiled.  ``You're always straight to the point, Director.''



``But the child is good?  A boy or a girl?''



``A boy.  Keith.''



``You've heard there are some third generation parahumans on record?''



``For a while now.  We knew they were being born anyways, right?''



``We did.  But nothing's official until it's on record.  But the point I was getting at was that there was apparently an incident.''



``Oh?''



``In Toronto.  A five-year-old manifested powers.  A third generation parahuman.''



Legend nodded, but he didn't respond right away.  He stepped forward to open a door for her.



``Everyone's alright?'' he asked, at last.



``No.  But no casualties.  The parents were outed in the chaos.''



``Sobering.''



She nodded.  ``The perils of being a superhero parent.  Your child isn't a third generation cape, I know, but there are always risks.  Still, I envy you.''



``How so?''



``Family.  I wonder if it is harder or easier to get through the day if you have people waiting for you at the end.''



``Yes.''



She smiled a little at that.



They entered the lab, and Emily Piggot very carefully measured the expressions of every person in the room when they noticed Legend.  Awe, surprise, amazement.  Sometimes ambivalence.



What could she take away from that?  If she were to promote one of them, should she promote one of the awestruck ones, or one of the taciturn?  The starry-eyed might be in the PRT for the wrong reasons, but the ones who were unfazed by the presence of one of the most notable heroes in the United States could easily be plants, hiding their emotion or simply too used to the presence of capes to care.



``The note?''



``No traces of toxins, radiation, powders or transfers.''



``Why the priority?  We get letters from cranks every day.''



``The man who delivered the message reported a fairly convoluted series of safeguards to protect the identity of the sender.  Apparently the man who gave him his instructions was given the note by a civilian, and ordered to find a random individual to deliver it to the PRT, all with compensation arranged.''



``You've tailed him?''



``Of course.  We doubt anything will come of it.''



``No.  It wouldn't.  Can you make out the contents without touching the envelope?  Can't be too careful.''



``We can and have.''  The technician handed Emily a paper.



She read it over twice.  ``Burnscar is dead, it seems, and Bonesaw won't be in the field for the interim.  God knows how quickly she'll recover, but it's something.''



``Good news,'' Legend said.



Emily wasn't so sure.  ``It's\ldots a change.''



``Not a good one?''



``The closing line reads, `Thanks for the help.'  I can't help but read it in a sarcastic tone.''



``The bug girl?  Skitter?''



Emily nodded.  ``Exactly.  As good as it is to have one more member of the Nine dealt with, this shifts the balance of power towards another group of villains.  It also serves to move up our deadline.''



``What do you want to do?''



``Call a meeting.  Protectorate and Wards.''



``Alright.''



\sectionbreak



She looked at each of the capes in turn.  Legend, Prism, Ursa Aurora and Cache were the outsiders, heroes on loan.  Miss Militia's group was more worn out.  Where their costumes had been damaged, stained or torn, pieces had been replaced from the generic costumes the PRT kept in stock.  Miss Militia had doffed the jacket but left the scarf with the flag motif in place.  She wore a black tank top and camouflage pants with a number of empty holsters and sheaths for her weapons.  Battery was wearing a plain black costume and goggles, while Assault had replaced the top half of his costume with similar odds and ends.  Triumph still wore his helmet and shoulder pads with the roaring lion style, but his gloves had been replaced with the same utilitarian, generic ones the PRT officers wore in the field.



The Wards, at least, were in better shape.  Tired, to be sure, but they hadn't been directly in the fray.  The patrol shifts were unending and they always had something to do.  Weld, Flechette, Clockblocker, Vista, Kid Win and Chariot.



She deliberately avoided looking at Chariot.  The mole in their midst.  Did Coil suspect she knew about the mole he'd planted?  Could she afford to assume he didn't?



Still, it would all be for nothing if she gave the game away.  Back to the matter at hand.



``We have three priorities,'' she began.  ``We take down the Nine, we regain control of the city, and we \emph{don't die}.''



She stressed the final two words, waiting to see their reactions.  Were any of her people thinking of performing a heroic sacrifice?



``There's no point in winning now if any of you die or get converted to the enemy side by Regent or Bonesaw.  Even if we were to defeat the Nine outright, through some stroke of fortune, I harbor concerns that we'd lose the city without the manpower to defend it.  It's a dangerous situation.''



She picked up the remote that sat in front of her and clicked the button.  The screen showed a map of the city with the spread of territories.



``The Nine have the advantage of power.  Not necessarily in terms of the abilities at their disposal, but in terms of their ability to affect change and shape everything that occurs.  They are our number one priority, obviously.  With them gone, if nothing else, I can hope that more capes will be willing to venture into the city to help out.''



``But we're operating with a deadline, and the Undersiders and Travelers have just moved it up dramatically.  The Nine posed their challenge, and they're losing.  There's now four 'rounds' of Jack's little game remaining.  Twelve days, depending on their successes and failures in the future.  I've talked it over with Legend, and we're both working under the impression that the Nine will enact whatever `penalty' they mentioned in the terms for their game.  Our working assumption is a biological weapon.''



There were nods around the table.



``In short, our worst case scenario is the Nine feeling spiteful or cornered, and deploying this weapon.  When we attack, we need to make it an absolute victory, without allowing them an opportunity.  Wards, I know you're not obligated to help in this kind of high-risk situation.  This is strictly voluntary, and I've had to discuss the matter with your parents to get permission to even \emph{raise} the subject, but I would value and appreciate your help on this front.''



The Wards exchanged glances.



``If you could raise your hand if you're willing to participate?''  She ventured.



Every hand except two was raised.  Chariot and Kid Win.



It did mean she had Flechette, Clockblocker and Vista.  The ones she needed.



``Thank you.  Rest assured, Chariot, Kid Win, that I harbor no ill will.''



``My mom wouldn't forgive me if I went,'' Kid Win said.



``I understand.  Now, the Nine are only one threat.  Let's talk about the others.''  She clicked the remote again.  ``Tattletale's Undersiders have the advantage of information.  We still don't know her powers, but we can speculate that it's a peculiar sort of clairvoyance.  She was able to provide us detailed, verifiable information on Leviathan after fighting him, even though she was only participating for several minutes before being knocked out.''



She paused. ``I believe this is why, in a matter of twenty-four hours, they were able to fight the Nine twice and win both times.  On the first occasion, they captured Cherish and Shatterbird, presumably enslaving the pair.''



``So they have Shatterbird's firepower and Cherish's ability to track people, now,'' Legend spoke.



Piggot nodded.  ``Skitter contacted us for assistance, as some of you will remember, and when we refused, the Undersiders took the fight to the Nine a second time.  Burnscar is dead, Bonesaw injured.  She's invited us to attack them in the meantime.''



``Why would we do that now when we turned down her offer to cooperate?''  Weld asked.  ``What's changed between now and then?''



``Communications will be up shortly,'' Piggot replied, ``We now have the consoles and trained employees ready to man them, and so long as we're going into this as a unit, we don't need to worry about other groups stabbing us in the back at any point during the battle while we engage the Nine.''



``Would they?''  Legend asked.  ``I have a hard time assessing their motives and morality.''



``I don't know.  \emph{Could} they?  Yes.  And that possibility is too dangerous, especially given what Regent can do.  The Undersiders do not pull their punches.  The Travelers, oddly enough, are more moderate, but they do have sixteen kills under their belt, due in large part to the sheer power at their disposal.''



``Let's not forget the incident in New York,'' Legend said.  ``Forty individuals disappeared in one night.  Investigation confirmed the Travelers were occupying a nearby location.  Chances are good that they were involved.''



``They're complicated, no doubt,'' Emily confirmed.  ``But for now, they're one knot in a very  tangled weave.  The Nine have power, the Undersiders have information.  Coil has resources that may even exceed our own, including a precog of indeterminate power.  Last but certainly not least, Hookwolf's contingent is one and a half times the size of our own, and he's absorbing the whites from the Merchants to his own group.  He commands a small army.''



``It's a considerable series of obstacles stacked against us,'' Legend answered.



``And few capes are willing to step in to help defend the city.  Credit to Legend and his teammates for joining us.  Thank you.''



The group of guests nodded.



``There's more.''  \emph{Time to see how much information filters through to Coil, and how he reacts}.  \emph{With luck, we might be able to pit one problem against another}.  ``Armsmaster's confinement was technically off the record, to protect the PRT in this time of crisis.  He escaped, and thus far, Dragon has not been able to track him.  Without official record or reason to arrest him, our measures are limited.''



``It's impressive that he got away from Dragon,'' Kid Win said.



``It is.  Thus far, he has eluded every measure she had in place.  Either he is much more crafty than even Dragon anticipated, keeping in mind that she's a \emph{very} smart woman, or Dragon helped him.''



That gave the others pause.



``Dragon's record of service has been exemplary,'' Legend spoke.



``It has.  And we've put an inordinate amount of trust in her as a consequence.  How many of our resources are tied into her work?  If she had a mind to oppose us, would we be able to deal with her?''



``We have no reason to think she's done anything.''



Emily waved him off.  ``Regardless.  Very little of this situation remains in our control.  Armsmaster is gone, the other major players are members of the various factions, and we remain in the dark about who many of them \emph{are}.''



There were nods all around.



She had them listening.  ``I have a solution in mind.  The higher-ups have approved it.  Clockblocker, you're going to be using your power defensively if things go south.  They aren't patient enough to wait for it to wear off.  You can protect yourself by using your power on a costume you're wearing, yes?''



Clockblocker nodded.



``Vista, I'm counting on you to help control the movements of the Nine.  Siberian is immune to powers, but not to external influences.  The timing will be sensitive.''



She clicked the remote, then turned her head to look at the result.  It was a warhead.



``On my command, a stealth bomber is prepared to drop payloads of incendiary explosives at a designated location.  We evacuate civilians from the area or lead the Nine to an area where evacuation is possible or unnecessary, then we drop a payload on site.  If they move, we drop another payload.  Clockblocker, you protect anyone that's unable to clear out.  Legend will ferry you to where you need to be.  Cache can rescue people as the effects wear off.''



``That's\ldots still not reassuring,'' Flechette spoke.



``You'll be equipped with fire resistant suits.  I ordered them in anticipation over fighting Burnscar, but the plan has been adjusted.  You'll all look identical, except for agreed upon icons, colors and initials on each costume.  Ones Jack and the other members of the Nine will not be able to identify, please.  There's a team ready to prepare the costumes at a moment's notice.  It will help mask the identities of those involved, and postpone any reaction from Jack over our having broken the terms of the deal.''



``But we \emph{are} breaking the deal.  Even if Legend's team doesn't get involved-'' Miss Militia started.



``The incendiary deployments will serve three purposes.  They'll forestall any biological attacks Bonesaw attempts, they'll force Siberian to stay put to protect her allies and they'll kill Jack or Bonesaw if she isn't able.  Humans aren't biologically programmed to look up, and whatever else Siberian is, she's still \emph{human} at her core.''



``And if Siberian does protect her allies?'' Weld asked.



``Flechette will see if her enhanced shots can beat Siberian's invulnerability.  Failing that, Clockblocker contains the woman.  His power won't work on her, but we can cage her in thread or chains that he can then freeze.  If we can do the same with Jack and Bonesaw, we can starve them out, or wait until they let go of Siberian.  If you're prepared, Clockblocker?  We can support you with relief teams.''



``If it means stopping them, I'm down.''



``Unless she's able to walk through \emph{that},'' Weld spoke.



``It's inviolable,'' Clockblocker said, leaning back in his chair.  ``I'd sooner expect her to fold the universe in half.''



``You're sure?''



``It's what the doctors say.''  Clockblocker said.



``And Crawler?'' Legend asked.



Piggot spoke, ``Legend, Ursa Aurora, Prism, Weld, Assault and Battery will occupy him until we can contain him.  He's still vulnerable to physics.  I'm hoping the white phosphorous explosive will keep him in the area long enough for us to put measures in place.  As I said, we can't afford to do this halfway.  If they get cornered, or if they think they'll lose, we run the risk they'll lash out.''



She glanced around the room at the fourteen parahumans present.



``We carry this out this evening, before any of our opponents catch on to our intentions and complicate matters with their own agendas.  That will be all.  Prepare.  See to your suits in the lab.''



She watched everyone file out.  Legend stayed behind.



``You're not saying everything,'' he murmured.



``No.''



``Fill me in?''



``Some of that is to mislead the spy in our midst.  We have a follow-up measure.''



``Does it pose a risk to this team?''



``It does.  Unavoidable.  I suspect Coil will inform Hookwolf and encourage the Chosen, the Pure and even Faultline's group to act.  Tattletale, I suspect, will know something's going on, and I intend to leak enough information to pique her curiosity.  It's in the moment that the villains enter the situation that the risk to our capes occurs.''



``But?''



``But we have a store of equipment we confiscated from Bakuda when we raided her laboratory.  Miss Militia deployed a number against Leviathan, but we have more.  Once the other factions have engaged, we bombard the area with the remainder in a second strike.  Our research suggests that several of these explosives can bypass the Manton effect.''



``This breaks the unspoken rules between capes.  And the truce against the Nine.  I don't like this.''



\emph{It's a world gone mad.  Do I have to join the madmen to make a difference?}



``Don't worry.  I'm the one who's going to push the button,'' Piggot answered.  ``And I'm not a cape.''
