





Bentley lunged in my direction, and I could feel my people backing away behind me.  I stood firm.  The mutant bulldog landed with both front paws first, the impact so heavy that spittle and moisture was flung from his massive body.



A low, guttural noise tore its way from Bentley's throat as he surged forward again.  I could hear yelps and shouts of alarm from the crowd behind me.



Wood splintered, cracked, and finally gave way.  Behind Bentley, the husk of a fire-scorched building collapsed.  Chains that had been lashed to the building's wooden supports trailed from the dog's harness as he bounded toward Bitch.  Of everyone present, only Bitch and I held our ground as the dog barreled into his master, practically bouncing with joy.



Bitch, for her part, wrapped her arms around his head as he lifted her off the ground.  ``Good boy!''



\emph{He's just a dog.  }Beneath the three-thousand-ish pounds of muscle and the exterior of tangled muscle and bone, he was still a dopey dog who adored his master.  Bitch had given him what he'd been yearning for since he was abandoned or abused in his past life.  She'd offered him the affection and companionship he'd been wanting for years.



I could relate.  Not in terms of Bitch, specifically, but I could relate.



``Get to work clearing that up!'' I ordered.  My swarm augmented my voice to carry it across the crowd of my followers.  There were twenty-two adults and twenty kids.  With Coil's assistance, I'd brought in work gloves and black hazmat suits, but most people were wearing only the lower body of the suits.  It was too warm for the full suits, and the masks were largely unnecessary.  Everyone was dripping from the rain, but nobody was really complaining.  I rather liked it; it was refreshing in the otherwise warm day.



A generator stirred to life a short distance down the street, and there was something of a rush as people hurried to get away from the intimidating presence of the big bad supervillains and their mutant animals.  That, and there was something of a fight to get the power tools.  There were only so many circular saws and chainsaws to go around, and anyone who didn't have one was tasked with carrying the cut wood instead.



I created a barrier of bugs to stop one of the teenagers from reaching for a circular saw.



``If you're under eighteen, you don't get to use power tools,'' I called out.  ``Priority goes to the people who know how the tools are used.  Able bodied \emph{adults} get second dibs.  Listen \emph{carefully} to the guys who know what they're doing, and work somewhere dry if possible.  We've had enough casualties, let's not have anything stupid happening with someone slipping or losing their grip in the rain.  If someone's being an idiot, tell Sierra, and she'll inform me.''



Sierra glanced at me and nodded.



I turned my attention to Bitch.



``You owe me,'' she said.  The rain had plastered her short hair against her scalp.  Her gang of four people stood by with dogs on leashes: Barker, Biter, a college-aged kid with the scars of four parallel claw marks running across his face, and a girl with her arm in a sling.  They didn't look \emph{scared}, like my people had, but they still didn't look fantastically thrilled to be in close vicinity to one of Bitch's dogs on full throttle.



\emph{Nevermind that you were the one that came here early. } ``Of course.  We'll get you and your people some lunch.''



She frowned.  ``Lunch?''



There was a bit of a pause.  I waited patiently as she considered the idea.



``Fine,'' she decided.



``Come on,'' I told her.  ``We'll go to my place while we wait for the others.''



While Bentley had been helping to tear down and dismantle the derelict building, I'd been contemplating how I'd leverage Bitch's early arrival to mend fences and rebuild some trust.  I'd decided on something simple, as that seemed to work best with Bitch.  I imagined that she hadn't paid a lot of attention to stuff like food as she took hold of her territory.  Odds were good that she'd asked Coil for a lot of easy food she could stuff in her pockets and eat on the go.  She probably wouldn't pay much attention to stuff like seasonings or variety in courses.



I'd recently spent some time looking back on our past interactions.  Her perspective toward me had zig-zagged between a kind of hesitant acceptance and hostility.  We'd met, she'd attacked me.  We'd gone to the bank robbery, and she'd been open and excited, only to do a one-eighty and start shouting at me after misinterpreting something I said.  Two steps forward, one step back.  Until I'd left the group and then been outed as an undercover operative a short while later.  That had been a good solid one-hundred steps back.



Recovering from \emph{that} breach of trust had proven far more difficult than anything that came before.  Not quite impossible, though; I'd apparently proved myself in the recent past, because Bitch was making an effort on her end.  She was here earlier than I'd asked, for one thing, and she hadn't murdered me when I asked for a hand with some things I couldn't handle with my own power.



She glanced back at her group and whistled once, making a `come hither' gesture.  I couldn't tell if she was signaling her dogs and expecting the people to follow or if she was treating her own people like she did her dogs.  She grabbed the chain at Bentley's neck and used it to lead him.



Barker and Biter looked pretty unimpressed, either way.  Barker especially.



We didn't talk as we made our way to my headquarters, and I was okay with that.  Every exchange between us was one more chance for me to inadvertently offend her, and the silence gave me a bit more time to consider how to tackle all of this.  I was used to feeling like I had to approach every conversation with a strategy, planning out what I was going to say so I didn't sound like an idiot.  That went double for Bitch, because a slip-up could set me back days or weeks in terms of our friendship.



\emph{Should friendship even be my goal?}  Maybe I was better off just trying to be a teammate.



If it was just for my sake, I could probably convince myself.  As it stood, though, I was thinking of Bitch.  I felt like I would be abandoning her to a pretty lonely existence if I didn't at least try.



I let them into my lair, after sweeping the area with my bugs to check for any observers, unlocking and opening the shutter.  Charlotte had experienced a few sleepless nights since the scare three nights ago, so I'd given her permission to take it easy here, with the warning that I'd have guests and would want her assistance.  She still looked a little wary as Bitch, Biter, and Barker entered.



``Hamburgers?'' I asked Bitch.  She nodded.  When I looked at her minions, they signaled agreement.  Good.  Easy and simple.



``Charlotte, would you mind?  Maybe fries, too, if you know how to make them on the stove?''



``I don't, but there's some in the freezer that I can do.  They aren't bad,'' she replied.



``Good.  When you have a second, some towels for the dogs, too.''



``Okay.''



I led the others into the sitting area on the ground floor.  With the shutter up, some dim light filtered through the rain-streaked windows.  Bitch was outside, tending to Bentley, who had yet to shrink to a more normal size.



I stepped outside to give her directions to where she could stow Bentley until he'd returned to a more normal size, pointing the way to the beach.  She marched off with the one-ton monstrous dog, not offering a response.



Which left me to deal with her people in the meantime.



Barker and Biter gave me something of a George and Lennie vibe, with the smaller guy as the brains of the outfit, the larger one as the big oaf.  While I didn't have any major clues to Barker's powers, Biter was clearly a physical powerhouse.  He stood over six feet in height with a severe underbite exaggerated by a metal bear-trap style band of metal around his lower jaw.  His teeth, I saw, were filed into points.  His costume featured spiked knuckle-dusters and a number of leather straps and belts over his clothes.  Each length of leather was studded with sharp spikes.



Barker was an inch or two shorter than me, his hair and beard cut short enough that there was more skin than hair showing.  His eyes seemed overly large for his face, with heavy lids and folds around them that made him look older than he probably was.  His `costume' consisted of a black sleeveless t-shirt, jeans and tattooing around his mouth.  I'd seen him in something more conventional when Coil had introduced him to us, but now the only sign of his parahuman nature was the faint smoke that curled out of his mouth.  Just going by his lack of bulk and short stature, I thought I might be able to take him in a no-powers fist fight.



I'd nearly forgotten about Bitch's henchpeople in the chaos of dealing with the Nine and all of the fallout that had ensued.  I realized I knew very little about them.



To my surprise, it was Biter who did the talking.  He had a low voice, and his words were muddled by some combination of the mouthgear and the underbite.  ``You get along.''



I folded my arms.



He spread his hands, ``How?''



``How do Bitch and I get along?'' I asked.



He nodded.



``I'm not sure I'm comfortable talking behind her back.''



The girl with her arm in a sling spoke up, ``She acts like she's frustrated with us.  And I think we're frustrated with her.''



``I don't want to be rude, but that's really her business with you.''  \emph{They're her property, her territory.  }If I screwed around with her minions or started something, it would effectively be stepping on her toes.



``You can't offer us any tips?'' she asked.



She looked so hopeful.  Damn it.



``I can, but it's going to sound pretty damn basic.  Be honest, be absolutely clear in what you're saying.  Be obedient, but be assertive.  Don't let her walk all over you or she \emph{will} walk all over you.  At the same time, if you think there's something worth arguing over, be prepared to fight tooth and nail for it, because you'll be in a weaker position if you fight over it and lose.  Respect her space and her things, and remember that she's your boss above all else.''



``She doesn't act like a boss,'' Barker said, and he made it sound almost insulting.  Puffs of the dark smoke spilled from his mouth with each word, but they seemed to carry further than cigarette smoke would.  It seemed to be tied to the stress or emphasis on the sounds that drove it forward.  ``She does her own thing and she leaves us to clean up \emph{shit}.''



``Adapt,'' I told him.  ``That's all I can say.  If you've proven yourself reliable, showed that you're willing to clean up after the dogs and take care of them without complaining, she'll test you in other ways.  That'll be your chance to prove you're useful.''



He sneered, looking at the girl and the boy with the scars on his face.  ``She's cutting \emph{them} more slack than she's cutting Biter and me.  We shouldn't have to prove anything.''



``What do you do?  Your powers.''



He looked up at me.  ``You want to see?''



I shrugged.



\emph{``Whore}.''



The puff of smoke that accompanied the word detonated like a small thunder-clap, mere inches from my face.  I flinched, but it hadn't been intended to harm.  Only to alarm.



He sniggered.  I'd never met anyone who really \emph{sniggered} before.



I could see how Coil thought Barker and Bitch would be a match.  I could \emph{also} see where there would be some friction between the two.



I sighed a little, watching as Barker looked to the others, then over at Charlotte, as if they'd be joining him in his amusement.  None did.  Biter earned a brownie point in my book by staying quiet and simply watching.



I caught my baton from behind my back and swung it underhand, still folded up, into Barker's chin.  His teeth clacked shut with percussive force, and I stepped closer to push at his upper body while hooking at the chair leg with my foot to pull it in my direction.  He toppled backwards, his head hitting the wall behind him.



I didn't have a full measure of his ability, but I \emph{did} know his mouth was his weapon.  It made me look weaker, but I stepped back so his legs and the chair seat gave me cover in the event that he decided to attack me.



For extra measure, I drew the bugs out of my costume and sent them straight for his nose and mouth.



He went bug-eyed as he sat up, coughing and sputtering in an attempt to clear the bugs from his airway.  After one rolling cough, he created another detonation in and around his mouth, obliterating a majority of the bugs I'd tried to gag him with.



I glanced at Biter.  He was still seated.  Good.  I'd somehow thought that the guy would be stepping up to defend his partner, making this a two-versus-one fight.



Barker was climbing to his feet.  I saw him falter, then start coughing again, gagging.



The capsaicin had kicked in.



``That's the sort of thing you have to watch out for,'' I told him, as he fell to the ground, writhing and coughing, tears welling in his eyes.  I kept my voice level.  ``You're in my house, my territory, and you fuck with me?  That's the sort of thing that would get you in your boss's bad books if you did it to her.''



``He has,'' the boy with the scars on his face spoke.



Barker only gagged in response.



``Guess that's why he deserves shit duty,'' I commented.  I leaned against the wall, folding my arms, my telescoped baton still in one hand.



Bitch had chosen that moment to return.  She stared at the scene.  Me standing idly by as Barker was curled up on the floor, wheezing and making pathetic noises, a few stray bugs crawling across his face.



She looked at me, glaring.



``He started it, I finished it,'' I told her.



She looked at Biter, who shrugged and nodded agreement with my statement.  Bitch seemed to accept that as answer enough.  She picked up his chair, moved it a few feet so it wouldn't be in Barker's way as he kicked and spasmed, and sat down.



``I'm surprised there's no objections about me attacking your partner,''  I told Biter.



``Your house, your rules, you said.''



``What do you do?  No demonstrations, please.''



``I make parts of myself bigger.''  He pointed to his mouth, then to the fist with the spike-studded knuckle-duster.  ``Open wide, swing with bigger hands.''



\emph{Nothing that would have been that great against the Nine.  }I couldn't blame Bitch for leaving them behind.



``Fair enough.''  I addressed the two unpowered individuals from Bitch's group.  ``And you two?  Why were you picked for her team?''



``I was just starting my first year as a vet before everything went to hell,'' the girl said.  ``Needed money to pay my boyfriend's hospital bill, was offered more than enough.  He got better a week ago, then broke up with me.  Not even a thank you.  Guess I'm still here because I don't have anywhere else to go, and I like taking care of the dogs.''



I saw an opportunity.  ``Did you have a dog growing up?''



``Greyhounds.  Eclaire and Blitzen.''



``Blitzen?  Like the reindeer?''



``No.  Like German for lightning.  And Eclaire is French.''



I could see Bitch was tense.  Something about this line of conversation?



I guessed what it might be and continued the questioning.  ``Why greyhounds?  Don't they need a lot of exercise?''



She shook her head.  ``No.  They're running dogs, but they only need about a half-hour of walking a day.  They work really well living in an apartment, which we were.''



``They howl,'' Bitch said.



``Only if they're unhappy,'' the girl protested.  She glanced down as Barker thumped on the ground with one fist, then looked up at Bitch and smiled a little, ``And ours were happy.''



Bitch seemed to accept that.



``Do you have a dog now?'' I asked.



She shook her head.  ``I don't have the money.  Or I \emph{didn't} have money, before Leviathan came.  Student loans and living expenses kind of ate up whatever I made.  I'm hoping to save up enough with the work I'm doing now.''



``You buying the dog?'' Bitch asked.  She seemed interested, now, but there was still a tension, as if she was waiting for the other shoe to drop.  One wrong answer, and this could turn ugly.  I could only hope the girl had the right answers.



``I kind of want another greyhound, because it's what I grew up with\ldots and you'll get greyhounds from an animal rescue ninety percent of the time.  There's one I'm pretty fond of that's in one of your shelters, but he's yours, of course.''



She'd taken my advice about respecting Bitch's ownership.  Good.



``Greyhound?  Chase or Ink?''  Bitch asked.



``Ink.''



Bitch frowned.  I tensed, ready to jump in and distract with some mention of food.



Grudgingly, Bitch said, ``Rather they have a proper home than stay with me.''



I could see the girl's eyes widen in surprise.  ``I didn't- um.  Thank you.''



``If I see him in some cage in a shelter after you've taken him home, I'm going to track you down and \emph{dismember} you,'' Bitch growled.



I could see from the expression on the girl's face that she believed Bitch.  Still, I saw her steel herself as she replied, ``If I fuck up, I deserve it.''



There wasn't much more I could do to help that conversation.  I had hope that this would set Bitch's underlings in the right direction.



While they continued talking, I stepped away to check on the hamburgers that Charlotte was cooking on the stove.



``Is he going to be okay?'' she asked me.



It took me a second to realize who she meant.  I looked back at Barker.  ``Yeah.''



``I mean, is he going to attack us?''



``I dosed him with pepper spray, basically, as well as a few stings and bites to add to the hurt.  That'll generally put someone down for half an hour, so I don't think he's a threat.  I don't think he's stupid enough to attack with Bitch and I here.''



She nodded, but she didn't look \emph{relieved.}  I would have asked what was up, tried to pry for more clarification on just why she hadn't slept well, or why she was so easily spooked, but I was interrupted by the vibration of my phone.



I stepped up into my lair to take the call.



``We're a few minutes away,'' Lisa told me, the second I picked up.



``Bitch is here already,'' I answered.  ``Come in the front door when you get here.''



``Righty-o.  Ta ta.''



She hung up.



I took a second to compose myself, alone in the second floor of my lair.  Dealing with people, the sensitive management of Bitch and her underlings, pretending confidence where I didn't necessarily have it, and thinking of all the little details that would help me convey the image of someone confident and powerful\ldots it was draining.  It meant standing straighter, having the answers, thinking two steps ahead and using intimidation and fear to prevent any argument or insubordination like Barker's little stunt.  It meant retaliating in excess to any slight or disrespect.



Barker had pushed me, I'd left him mewling like a baby.



At the same time, I faced a dilemma on the opposite end of things.  I wanted to help people, and I wanted to build friendships with the others.  With the way Bitch sort of mandated that I go the extra mile, it was hard to be nice to her without seeming weak to others.



Well, what they didn't see didn't hurt them.



I stepped downstairs.



``Bitch?'' I asked.  ``A word?''



She frowned, glancing at the food.



``We'll be done before the food is,'' I promised.



She followed me up the stairs.



``It's not complete,'' I admitted, walking over to where I had fabric draped over a workbench.  I picked up one piece and flicked it out.  ``I just figured you'd want to see it and voice any complaints before the others got here, so your voice doesn't get drowned out.''



She took it from my hands.  It was a jacket, not dissimilar to the one she'd lent me once upon a time, but it was naturally lighter.  There was a hood with a fluffy fur border at the edges, extending around in front of her shoulders.  Besides the zippers and buttons, the fur was the only thing I hadn't made myself.



``I dyed it dark gray.  I figured if you wanted it any color, you'd want it something dark, so I can tint it dark red, dark blue, dark green, or whatever you want.''



She stared at it, her forehead creased.



``It's spider silk.  Tensile strength like steel, but flexible enough to resist wear and tear that steel wire would experience.  And it's lighter than the steel would be.  Knives won't cut it.  I figured you'd want a heavier feel, judging by the jacket you lent me before, so I put rectangular panels of armor in between the inner and outer layer to give it more substance.  I originally meant for there to be an undershirt or something you can wear to protect your upper body for when you don't have it zipped up, but I kind of cannibalized it for my own costume, after I burned my legs.  I'll have the shirt ready for you in a week or two.  Here, there's leggings, too.  They survived.''



I picked up the leggings.  Unlike the jacket, they were skin-tight.



``I don't wear tights,'' she said.



``I thought you could wear them under your pants if you were expecting a serious fight.  I gave you an inner layer with a really fine weave for the inner thighs, for when you're riding, so there's less chafing.''



``Uh huh.''



``I went out of my way to give you lots of pockets like you had in the other jacket.  I don't think it'll be too hot.  There's zippers in the armpits so you can ventilate some cool air inside, and you can detach the hood if you want, but I liked how it looked with the fur.  I'm planning an inside liner for when it's-''



``It's fine,'' she interrupted me.  ``Stop talking.  It's good.''



``Yeah?  I didn't get a chance to get your measurements, so I went by memory, based on the jacket you lent me.''



She pulled it on and adjusted the front.  ``Fits fine.''



``Here,'' I said.  I turned around and grabbed the next piece.  I handed it to her.



She turned it around in her hands.  I'd cheated and formed the base sculpt out of chicken wire, covering the remainder with layers of dragline silk and painting the end result.  It was, as close as I'd been able to manage, a recreation of what her power did to her dogs in the form of a mask.  Except I'd made it half human and half dog.



``Looks like Brutus,'' she said.



I didn't see it, but I didn't see fit to correct her either.



She pulled it on.



``It's just a little bit flexible, if you want to bend any bits that are rubbing in the wrong place, or shape it to fit your face better.''



``It's fine,'' she said.  She adjusted her jacket again.



``If you want me to change anything-''



``No.''



Her refusal was so curt it gave me pause.  I couldn't tell if she was upset or happy.



I forced myself to keep my mouth shut.  I'd give her a few seconds to let me know either way.  If she didn't, I was ready to escape by pointing out that lunch would be waiting for us.



``You made stuff for the others?''



``Yeah.''



``But I didn't ask for it.  I told you to fuck off when you asked me for my measurements, remember?''



``I made it anyways.''



She adjusted her mask, turning it so it hung off one side of her head.  She was glowering at me.  ``Why didn't you listen when I told you to fuck off?''



Two ways I could interpret that question.  ``Don't worry about it.  Look, the hamburgers will be ready soon\ldots'' I trailed off.



An awkward silence reigned.  I turned to head downstairs.



``What do you want for this?''



I looked over my shoulder.  ``What?  Nothing.''



``You're trying to get some favor from me.''



``No, I'm really not.  It might feel like it, with the timing and what we're going to talk about with Lisa and the others, but it's really not.  You're free to argue and disagree with me or the rest of us, just like usual.  The costume's a gift.''



``I don't get many gifts.''



I shrugged.  What was I supposed to say to that?  I couldn't help but feel that if I were a little more socially adroit, I'd have had a snappy answer.



She kept talking.  ``All of the stuff I've gotten, it's been with strings attached.  Used to get gifts from one of my foster dads,'' she paused.  ``And I get the money from Coil.''



``Those aren't really presents.  They're more like bribes or enticements.  Really truly, this is no strings attached.  You can act like you normally would, I won't expect any different.''



Again, that glower.



I swallowed.  ``Wear it or don't wear it.  It's okay either way.  It's not a big deal.''



``I'll wear it,'' she said.



When I turned to head downstairs, she followed.



\emph{I guess that means `thank you'.}



We were greeted by the others in the kitchen.  There was just enough time to grab and prepare our burgers before the others arrived.  Grue, Tattletale, Imp, Regent and Shatterbird.  They turned down the offer of food, and together, we ventured back upstairs.



With everyone gathered in my headquarters, I handed out the costumes.  Like Bitch's, the other costumes were in various stages of completion, primarily with minor details missing or askew.  I ate while the others tried it all on.



Lisa's costume was virtually the same.  The complicated aspect had been maintaining the crisp differences in color without any bleeding of black into lavender or vice versa.  There'd also been the issue of getting the mask to fit her face well.  I'd accomplished the former by making the black and lavender pieces separately and attaching them to a gossamer-thin sub-layer when I was done.  We had the boys and Shatterbird turn away while Lisa and Aisha changed at one end of the room.  The mask was a failure, it didn't sit right around the eyes, but I was left with an idea of what to do.



Grue's costume was not unlike his motorcycle leathers in terms of thickness and design, making him one of the most heavily armored of our groups in terms of the amount of material he was wearing.  His headwear was the part I'd changed the most: I'd modeled the face-plate after a figurine he'd bought at the market.  It was a step away from the visor he'd worn up to now, more demonic than skeletal.  The only real trick there had been making it non-porous enough that his darkness wouldn't bleed through.  A quick experiment proved that my efforts had turned out alright.  In costume, the face-mask down, the darkness framed his mask but didn't cover it unless Grue forced it to.  A demon's face in dark gray in a vaguely human-shaped twist of darkness.



For Regent and Imp, I'd settled on bodysuits and masks.  Regent would wear his beneath his costume and Imp would wear hers as a simple black bodysuit, complete with a scarf and the horned mask Coil had provided.



There was more to do: belts, Imp's scarf, Tattletale's mask and Bitch's shirt, not to mention finishing my new mask, and my plans for different masks for our various minions.



When we'd been fighting the Slaughterhouse Nine, I'd lamented the fact that I hadn't better outfitted the team, and people had been hurt where the costumes would have otherwise protected them.  In the days I'd had to wind down, focusing on getting people organized and working on cleaning up the area, I'd been in range to get a serious effort going on the costumes.



I was satisfied with this.



By all appearances, they were too.



``Safe to turn around,'' Tattletale told the boys.



They did.  I gestured, and people found seats in the various chairs.



``Feels like we're different people than we were an hour ago,'' Imp said, looking around.



I considered her words.  ``I appreciate the sentiment, but I think it's more accurate to say we're different people than we were a \emph{week} ago.''



There were some nods.  I glanced at the scar on Tattletale's cheek, at Shatterbird, who stood obediently behind Regent, and at Grue, who had transformed more than any of us.



And I couldn't forget the change I'd undergone, even if I didn't have the objectivity to nail down exactly what about me was different from a week ago.  Sure, my costume was different, and I had the three hundred pound beetle that was resting on the roof.



``You wanted to touch base?'' Brian asked, after he'd pulled off his mask.



``I had some words with Skitter,'' Lisa answered.  ``I think it's about time we all got on the same page.''



``In terms of tactics?''



Lisa shrugged, ``There's that.  I think working independently is kind of throwing us off, and it leaves us weak against any coordinated attacks from the Chosen.  We work best when we complement one another.''



Alec shrugged.  ``Okay.  That's easy enough to arrange.  Not really a reason to throw a major group meeting.''



``There's something else,'' I said.  I swallowed, looking at Regent, Imp and Bitch.  ``I've already talked about this at length with Lisa, and I've discussed it some with Brian.  This isn't an easy topic to broach, because it sort of fucks with the team's status quo.''



That had their attention.



``I guess the question is, how keen are you guys on continuing to work for Coil?''



``Are we talking quitting in the short-term or what?''



``I don't know exactly what we're talking about, because so much depends on how you guys respond and how things unfold in the next while,'' I said.  ``But this thing with Dinah, I'm not happy with it.  I know Lisa and Brian have their issues with that, even if they don't share my perspective in how culpable we all are in that.''



``I'm not responsible at all,'' Aisha pointed out.



``Aisha,'' Brian's tone was a warning.



``Just saying.''



``You aren't responsible, I know,'' I told her.  ``I get the impression you'd side with Brian, Lisa and me if it came down to it.  The people I'm really directing this question at are Alec and Rachel.  I'm under the impression they're the least invested in helping Dinah out, and they're most interested in what Coil has to offer.''



``Doesn't Brian have a stake in this?'' Alec asked.



Brian shrugged.  ``Coil approached me a few days ago about increasing my pay.  I think he knows I'm not that reliant on him anymore.  I got into this because I wanted to get Aisha away from my mom.  With the way things in the city have been turned upside-down, I know \emph{and Coil knows} that I don't need help.  The fact that I can say I've got money saved up, I can arrange to get a place and Aisha's safe and sound with me?  That's almost enough to decide the court case as is.''



``And mommy's on a bender,'' Aisha said.  ``Don't think it'll end anytime soon.''



It was odd, but Brian looked more upset at hearing that than Aisha was about saying it aloud.  Hadn't he grown up with his dad?



``So it's really down to you two,'' I addressed Alec and Rachel.



``If I were to say I wanted to stick around?  That I like the status quo?'' Alec asked.



``That's fine,'' Lisa said.  ``You'd be an asshole and a prick, but we'd work around you.''



``That's vague,'' Alec commented.



``We can't exactly share our game plan with you if we're going to wind up on opposite sides,'' I pointed out.



``It's a hassle.  Why make things complicated for \emph{all of us}, because \emph{one} member of our group has a moral quibble?''



``A preadolescent girl was kidnapped, \emph{with our help}, and she's spent the last few months in a dungeon, drugged out of her mind, all so Coil can use her power,'' I said.  ``That's not a \emph{quibble}.''



Alec sighed dramatically.  ``I'm just pulling your legs.  World's going to end in a couple of years.  Won't kill me to help you make peace with yourself before it does.''



There was a long pause where nobody spoke.



``\emph{Nice}, Alec.'' Brian said.



Alec chuckled.  ``What?  It's true.  That Dinah kid said it was.  Don't pretend it's not going to happen.  Might as well live it up before everything goes to hell in a handbasket.''



``There's a chance it won't,'' I replied, my voice quiet.  ``And with the sheer variety of powers out there, there's got to be an answer.''



``That optimism's bound to be wearing thin by now,'' Alec commented.



``Enough,'' Brian said.



``Why are you guys freaking out?  Because I'm calling you out on your willful blindness?  The world's gonna end, and I'm okay with that.  \emph{Therefore} I'm saying I'll go along with your plan, whatever it is.  Why argue with me?''



Brian sighed.



``Bitch?'' I asked.  ``I know Coil's set up your dogs in those shelters, and we'd be asking you to potentially lose that, depending on how this plays out, but\ldots''



``I've managed without money before,'' Bitch said.  ``Smarmy bastard conned me.  Promised me I'd be left alone if I joined the group.  That hasn't happened.  If he thinks I'll forget that because of what he's given me, I'd like to see the look on his face when he finds out how wrong he is.''



``Thank you,'' I said.



``So we're all in?'' I asked.



``It was fun,'' Alec shrugged, ``That's why we got into this, wasn't it?  Easy money, fun, get to do what we wanted.  No pressure, no responsibilities.  It's become something else.  So maybe we end that.''



``I don't necessarily want to end it,'' I said.  ``I'm not talking about taking Coil head on, and I \emph{do} want to preserve my territory, if I can help it.  It's helping people.''



``So what do you want?'' he challenged me.



``For right now?  I mainly wanted to know you're on my side.  I really appreciate that you are,'' I said.  I looked at Bitch and repeated myself, ``Really.''



``And for the future?''



``We've got an awfully small window,'' Lisa said.  ``One and a half weeks, roughly, before Dinah's power is back online.  Once that happens, Coil becomes a thousand times harder to take on.  There's the mayoral elections, the question of whether the city gets condemned-''



``What?'' I cut in.



``It's arguably more expensive to fix the problems here than it is to abandon the city entirely.  Depends on what the consensus is from the President and all the other folks in charge.''



``If that happens, what will Coil do?'' Brian asked.



``Leave.  Start over somewhere else, transporting any resources he can, leaving behind all liabilities.  He might bring some of you with him, offering some hefty bribes.  Somehow I don't think he'll bring Skitter.  Even my own currency is running pretty thin,'' Lisa shrugged.



``He can't afford to lose you,'' Brian said.  ``You're too dangerous as an enemy.''



``Oh, I think he's studied me enough to feel pretty confident he can off me if he wants to,'' Lisa said. ``Trick is making it a sure enough kill that there's no chance of it backfiring on him.''



``And me?'' I asked, feeling a pang of alarm.



``He knows your weak points.  The gaps in your power, your dad, your identity, your morals.  You already know that.''



I did, but hearing it said so clearly, it was one of those cases where having the details laid out in front of me didn't make me feel more confident.



``So this is going to be a different kind of fight,'' Brian mused.  ``It's about control and subterfuge.  If he figures out what we're doing, if we clue him in, he's probably better equipped than any of our past opponents when it comes to knowing how to deal with us.  If the city gets condemned, we're boned.  \emph{And} if Dinah gets her powers back, he'll be impossible to beat.''



``That's the gist of it.  Even \emph{I} don't know what he has planned for his endgame, here.  It's looking pretty ugly, to be honest.''  Lisa counted off the points on her fingers.  ``The Chosen will be gunning for us, Coil's got a small army of pretty excellent, well-equipped soldiers at his disposal, he's got some pretty fucking heavy hitters with the Travelers, the heroes are going to be going into overdrive to establish some sort of control and last but not least, he's \emph{Coil}.''



``Well,'' Alec said, chuckling a little, ``At least we'll have something to help pass the time while we wait for the world to end.''





