





One thing at a time.



As much as I wanted to make it a focus, taking care of my territory was something I had to handle in my downtime.  I felt guilty; I'd left my people to handle things on their own, I'd failed to arrange the cleanup of the bodies Mannequin and Burnscar had left behind.  I hadn't made arrangements for food, fresh water or accommodations.  I wanted to make it up to the people who had stuck by me, or at least the people who hadn't left, but this wasn't one of the instances where I could let my emotions dictate my priorities.



We had a mess of things to do and a limited amount of time to work with.



After departing from our meeting, we'd taken the afternoon and evening to handle our personal affairs, agreeing to start on the major stuff in the morning.  Bitch had to take care of her dogs, Regent was toying with gangs in his territory by puppeteering their leaders, and Tattletale had her various spies and scouts to keep in contact with.  Things were a little less busy for myself, Grue and Imp: I'd tended to my territory, ensuring that the cleanup was going well and that the major concerns were being addressed.  Grue and Imp had taken the afternoon and evening to try to catch up on sleep.



Except we hadn't been able to break away from planning, and just going by his participation in our exchange of texts and calls, Grue hadn't managed to rest much.  We'd arranged plans, discussed priorities, sent messages to Coil, tracked down information from our various underlings, and in the doing, we'd managed to hash out a general game plan.



With a hundred problems we needed to handle, we'd agreed the most important thing was to deal with the most \emph{inevitable} ones.  There was no point in working out a complicated and involved attack plan against Coil if we didn't wind up fighting him.  There \emph{was} a point in dealing with the Chosen; they were bound to attack us at some point, regardless of how future events unfolded.  Better to take the fight to them.



``Whatcha thinking, dork?''



``You're still calling me that?''



Regent chuckled.  He was walking down the center of the street with Imp.  I was keeping to the sidewalk out of habit, and because the raised concrete path was fractionally higher, so I wasn't wading in quite so much water.



``Just thinking about priorities,'' I told him.



``Yeah, Tattletale kept trying to rope me into the planning phase last night.  Not my thing.''



``I wouldn't have minded,'' Imp said.  ``I wouldn't have anything to contribute, but I'd like to follow along.  And I can't figure out my niche in the group with the trio being so\ldots trio-ish.''



``Trio-ish?'' I asked.



``Tattletale, you and my brother.  Making all the plans, you've got the nemeses\ldots'' Imp paused.  ``Is nemeses a word?''



``Yeah,'' I said.



``\emph{And} you three have the brains, of course,'' she stabbed a finger in my direction, as if it was an accusation, ``Which leaves Regent, me and Bitch, following along, expected to obediently do as we're told.''



``Let's quit and start our own group!''  Regent said, throwing one arm across Imp's shoulders and gesturing dramatically with the other as he continued, ``Regent, Imp, and Bitch, the Othersiders, a spin-off team.  And we'll stick with Coil while the others turn traitor, and we'll have this epic fight\ldots''



Imp took his cue, ``And Brian and I will go head to head, and it'll end in this dramatic moment where he says something pretentious--''



``Et tu, sis?''



``And then I'll say `Yeah, it's me' and finish him!  No mercy.''



They were playing off one another, joking.



\emph{And he calls me the dork?}



I ignored them up until we met up with Tattletale.



``No Grue?'' she asked.



``He's tired,'' Imp said, shrugging free of Regent's arm, which had stayed in place since they began their play-acting.  ``Not sleeping these days.''



``We should address that soon,'' Tattletale said.  ``We've seen how mistakes happen when some of us get too fatigued.  With the way things are stacked against us, we could wind up with another few days of concentrated activity, and running on empty from the start could spell bad things.''



She glanced at me.  Fine, I'd own up to it.  I'd fallen into that trap.  I nodded an agreement.



``And you?'' she asked me.  ``You're good?''



``Guilty about leaving my people to their own devices,'' I admitted, ``But I'm glad we're working through this stuff.''



``Speaking of,'' she said.  ``We've got the mayoral elections coming up in a week and a half.  They were thinking about canceling them, but with the Nine gone, they're apparently wanting to get things closer to normal.''



``What does this mean for us?'' I asked.



I caught a glimpse of Imp nudging Regent, in a `see, see?' kind of way.  She muttered something about the trio.



``On the upside, Coil has two agents as mayoral candidates, so he'll be focused on that.  On the downside, it's another thing we have to take into consideration.  We could throw a wrench into that situation, to slow him down in his takeover and buy ourselves time to leverage the situation to our advantage, but I'm wondering if it's really worth it with our other time constraints.''



``The primary one being Dinah getting her powers back,'' I said.  I turned to the other two, ``Are you wanting to chime in instead of poking fun?''



``I'm good,'' Imp said.  Regent chuckled a little.



Tattletale said, ``I've been trying to figure out what's been happening with the Chosen and Purity's group.  The white supremacists keep losing leaders.  Kaiser got offed by Leviathan, now we've got a brainwashed Hookwolf running off with the Nine.  The natural thing for the group to do would be to fall in under Purity, but there's some snags.''



``Some Chosen thinking they want to be leaders?'' I asked.



``There's that.  Stormtiger and Cricket have been Hookwolf's followers for a while.  I could see how they might feel that it was their due to get a turn.  There's also the fact that Hookwolf was probably engaging in some propaganda against Purity, in case she tried poaching from his team.  So you've got the overall group split between the Chosen and the Pure we've had for a few weeks now.  Then you've got another split within the Chosen, with the loyal and the brainwashed, and the, um.  Not sure what to call them.''



``The free thinkers?'' I offered.



``If you can call a neo-nazi a free thinker,'' Tattletale conceded.



``So it's a prime opportunity to strike, then,'' I concluded.



``Maybe.  Or maybe they're in the same straits as us.  They could be feeling the same kind of pressure from multiple directions.''



``Something to keep in mind,'' I said.



``Something to exploit?''



I glanced at her in surprise, and she shrugged.



``Elaborate?  You're not suggesting we ally with them, are you?''



``Fuck yes!'' Imp skipped halfway across the road to join us.  ``Finally, an argument I can get into.  No way are we allying with the skinheads.''



``Are you taking this seriously?'' I asked her.



``Totally one-hundred-percent serious.  I'm not cool with working with them on any level.  I've put up with their racist asshole kids giving me a hard time at school, I put up with their racist asshole \emph{adults} throwing slurs and swear words at me when I'm walking down the street.''



``I'm not talking about working with them,'' Tattletale said.  ``I'm talking about a ceasefire.  We broker a deal, agree to leave them alone if they leave us alone, they can hold their own territory without worrying about us, and they extend the same civility to us.  It gives us a chance to do what we need to do.''



``Still not cool,'' Imp protested.  ``It gives \emph{them} a chance to do what they want to do, which is making life hell on anyone that isn't straight, white and Christian.  Or whatever you call people that worship those viking gods.  They like naming themselves after those guys.''



I looked at Tattletale, ``I can't argue with her point.  The first part.''



Tattletale frowned.  ``I'm trying to think about what's easiest to achieve while clearing up the most problems.  I already got in touch with New Wave and got them to chill out for a bit.''



``How'd you pull that?'' Regent asked.



``Lady Photon was wondering where her nieces went.  I told her that Panacea was healing Glory Girl but she still wanted her space.''



``Hmm,'' I offered, to give an indication I was listening.



``It isn't true, or I should say it isn't the \emph{whole} truth, but we tried to reach Panacea and she turned us down again and again.  It's a shame, but what can you do?''



Amy had crossed my mind as I'd reflected on the various encounters with the Nine, and I'd thought about going to look for her.  Having her in the group would be invaluable, no question.  Even touching base with her could leave us options if someone got hurt or if we needed resources.  That said, the major issue was that I couldn't be sure she'd actually join or even listen, and we were trying to operate with certainties.  I couldn't afford to go when it meant potentially wasted time.



Better to be in my territory, for morale, for organization, and to keep working on the costume bits.  It also let me eat, sleep and take care of Atlas – stuff I tended to forget about.



Thinking about Atlas reminded me of one thought I'd had during our downtime.  ``It'd be fantastic if we could get a tinker in the group,'' I said.  ``Between Bakuda, Armsmaster, Mannequin and Bonesaw, I'm sort of starting to appreciate what they bring to the table.''



``What you see there are the end results,'' Tattletale said, ``You have to realize how much time they're spending building stuff, or time spent building tools to build better stuff.''



``Bonesaw did plastic surgery on seven people, performed brain surgery on Cherish and then trapped her inside a pod that could keep her alive for years or decades, and as far as I figure it, even if they got their hands on an all-terrain vehicle, they can't have had five or ten minutes to do it in.  That doesn't amount to much prep time.''



``Some to build and program her mechanical spiders, but yeah.  She probably wouldn't need as much time as you'd think.  Probably didn't even have to put Cherish's head back together after doing what she needed to for the surgery, for example, if she was going in the pod.''



``\emph{You're} almost a tinker,'' Regent told me.



``Not really.''



``You made these rags,'' he pulled down his collar to show me the skintight costume beneath.



``\emph{Rags}?  If you don't want them, I can use the material.''



He laughed.



``I don't think I'm anything like a tinker, though.  I just realize my power's not that strong, so I wrack my brain to think of ways to expand it.  I make the most of the possibilities available to me, while a tinker \emph{creates} possibilities.''



``I'm getting what you're saying,'' Tattletale smiled.  ``You liked having Panacea around as a pseudo-tinker, huh?  The way it expanded your options?''



I shrugged, ``Goes without saying, doesn't it?''



``But you especially, given how you think.  It's a shame that there's not really any tinkers around that aren't already committed.  Unless you want to make a point out of recruiting Leet?''



There was a bit of a pause as we all considered the idea.



We simultaneously broke into laughter.



``Come on,'' Tattletale said, ``Let's get down to business.''



Beyond our short detour to meet up with Tattletale, we'd primarily been focused on heading towards Regent's territory.



As if they knew Regent didn't have the forces to retaliate or respond in kind, the Chosen had decided on an underhanded means of attack.  If you could call it that.  The Chosen's wolf-head gang tag and swastikas marked every available surface.



A snub, an insult.



Shatterbird descended from some distant point high above us, landing in the middle of the College, Regent's territory.  It was the middle ground between Downtown and the Docks, and the buildings were a mix of quaint housing and stone buildings.  Or they had been.  Most were ruins now.



Dust and sand stirred around us.  It coiled around Shatterbird, then streamed against the offending pieces of artwork.  Housepaint and whitewash peeled and disappeared, flecks of spray paint were gradually worn away, and concrete was chipped.



In less than a minute, the area was clean.  Not only was it free of the spray paint, but walls were left looking cleaner and newer than they had in years, maybe decades.



``Nifty,'' Imp commented.



``Why spend a few hundred bucks on a sandblaster when you have a Shatterbird?  Who's a good little power tool?''  Regent gave Shatterbird a pat on the cheek.  ``You are.  Yes you are.''



``Stop that,'' I said.



``What?''



``That's uncalled for.''



``It's \emph{totally} called for.  Are you bothered I'm calling her a tool, or are you bothered I'm mocking her?  Because she \emph{is} a tool, you know.  In more than one sense.''



``You don't have to mock her.''



``Why?  Because we should be respectful of the poor widdle mass murderer's feelings?''  He snapped his fingers, and Shatterbird covered her ears, shutting her eyes.  ``There's a \emph{reason} I'm doing this, believe it or not.  You aren't the only one who can have ideas about finding some special angle in your power.  Her best bet at breaking free is if she has a strong enough emotional reaction while being far enough away from me.  I'm irritating her because I want to keep her emotionally drained.  That way she won't be able to put up a good fight when she \emph{does} get a chance.''



``There's got to be a better way of doing that.''



``Sure.  Tell you what.  Next chance I'll get, I'll take her to my lair, sit her down and torture her until her mind breaks.  Heck, it wouldn't even be that hard.''



``You--'' I started.



``He's being facetious,'' Tattletale interrupted.



Regent rolled his eyes.



``The alternative is killing her,'' he said.  ``But that seems awfully wasteful when she's giving us some much-needed firepower and deterrence.''



``I'm not saying torture her, and I'm not saying kill her.  I'm just asking you to treat her with respect.''



Shatterbird spoke, startling me.  ``Hi!  I've killed hundreds of people and maimed \emph{thousands}.''



``I get your point, Regent.  Stop that.''



Shatterbird smiled wide, the expression so fake and cheery it was disturbing to see.  I tried to ignore her as she continued staring at me.



As an idle thought, I noted that her teeth were in surprisingly good shape.  It made me wonder how the Nine took care of their teeth.  Did they threaten some dentist and force him to do fillings and whitenings?  Or did Bonesaw handle that?  It was odd to think about.



``Okay, we've got Shatterbird for some firepower, you've got a swarm, Skitter?''



My bugs weren't \emph{condensed} into a swarm, but I had a good number.  ``I'm set.''



``Can you find them?''



My bugs searched our surroundings.  ``There's people, I'm just not sure they're Chosen.''



``Where?''



I pointed.  ``Six there, belowground.  Eight there, on the far side of the building where it isn't caved in.  Five there, front room, drinking alcohol, I think.''



``That group,'' she gestured to the first one I'd indicated, where people were gathered in a basement or cellar.  Some stone building with sandbags around it to keep the floodwater at bay.  ``Ages, genders?''



``I can't say about ages, but two are below average in height, smaller across the shoulders.  So probably younger.  Two female, one male.''



``Are they agitated, busy?''



``They're annoyed because of the houseflies and mosquitoes buzzing around them, but I don't think they've realized it's me.''



``Just trying to figure it out.  The quality of the lodgings here is pretty miserable compared to some areas close by, then if I go by the graffitti and the placement thereof\ldots yeah, it's them.''



``All of them or just some of them?''



``Everyone present is a member of the Chosen.''



``You're sure?''



``Yeah.  Nobody's going to hang out here otherwise.  Doesn't fit.  Even if I discount some of the evidence that's leading my power to the conclusions it's finding\ldots yeah.  I'm sure.''



``Then cover up,'' Regent alerted us.



I pulled the short cape over my head to cover my hair.  I could see Imp wrapping her scarf around her head with the same idea in mind.  Tattletale, for her part, pulled on the spider silk balaclava I'd made as a trial run at something for my minions, then donned a pair of goggles.



``Go, Skitter,'' Tattletale spoke.



We attacked.  My bugs flowed into the spaces where I'd found the people.  In one moment, they were simply crawling on them, the next moment they were under attack, being bitten, stung, scratched and smothered.



As usual, I kept the wasps and bees from contracting their abdomens to force the venom out.  It would hurt, but the risk of anaphylactic shock would be minimal.



They fled, running for the outdoors.



I gave them a second of reprieve.  A few seconds where they could catch their breath and think they'd escaped.



``Your turn,'' I told Regent.



Shatterbird attacked, calling forth a light flurry of glass shards.  There weren't many, far less than I had in the way of bugs, but our enemies couldn't defend against them.  My mosquitoes could smell blood as the shards sliced thin papercuts into their skin, impaled their cheeks and hands.



``Don't hit any vital organs,'' I said, ``Or arteries.  Keep it confined to the outer edge of their body.''



``You're so \emph{finnicky},'' Regent commented.



``If you kill them, this situation becomes something totally different.  They'll have a vendetta against us, and any friction within their group is going to take second seat to getting revenge.''



``I'm not saying I \emph{won't} be careful,'' Regent sighed.  ``I'm saying you're being picky.''



A section of building floated across the street to land at the midway point between Shatterbird and our targets.  There were nearly twenty of them, and one of them was Rune.  Okay.



Shatterbird extended her arms out to either side.  The pelting hail of glass shards split in two, each half arcing well to the left and right, circumventing the obstacle entirely.  He stepped up the intensity a notch.



``Feels like we're going easy on them,'' he said.



``Just weeding out the foot soldiers.  If we can eliminate anyone with powers, so much the better.''



I nodded.  We'd made our point with the glass shards.  I set my bugs on them once again.



No point in playing fair, really.



One by one, they collapsed, losing their balance and falling, or simply giving way under the pain.  The second one of them went limp on the ground, curling up in the fetal position or trying to cover themselves in their clothes, I let up.  For everyone else, I made the bugs a \emph{little} more aggressive with every passing moment.



``They're going to retaliate soon,'' Tattletale informed us.



A cloud of mist erupted and began to expand, squashing my bugs.  That meant Fog was here.  And if he was here, Night would be too.  Night and Fog, \emph{Nacht und Nebel}.  I could sense someone who could have been her, running away from the collection of people.



``Rune, Night and Fog so far,'' I said.



``That's two different groups.  Rune could be looking to join the Pure,'' Tattletale spoke.  ``Purity's not here or she would have responded already.  You're not sensing anything that could be Crusader?  Your bugs wouldn't be able to pass through his astral clones.''



``No Crusader.''



I sensed someone my bugs were unable to hurt.  He ran forward through the swarm, the hail of glass and Fog's cloud.  ``Incoming.  Not Night.''



Victor.  He was a talent vampire, stealing people's trained skills, keeping them if he held on to them long enough, and leaving that person temporarily bereft of whatever skill they'd spent their lives learning.  People like him had a tendency to pick up martial arts, parkour, weapons training and other combat skills.  He tended to pair up with Othala, the girl who could grant powers, meaning Victor \emph{also} had super speed, super strength or invincibility.  If he was wounded, she could give him regeneration instead.



But her power demanded that she touch whoever she was using it on, and it limited her to granting one power at a time.  If he had invincibility, it meant he didn't have super strength, pyrokinesis or any of that.



I started tying him up in silk, drawing the lines out with my spiders and carrying them with flying insects.



He didn't make it halfway to us before stumbling.  A minute later he was caught.  I began layering it on him, thicker.



``Victor down.  Othala's somewhere, only big problems are Night and Fog.''



``Okay.  How confident you feeling?''  Tattletale glanced at me.



``I could try my hand at dealing with Night.  Not sure about Fog.''



``Regent?''



``That's cool.''



``Going to see if I can bait them,'' I responded.  ``You guys get back some.''



``Play safe.''



Our last run-in with Night and Fog had been ugly.  That had been months ago, and we'd basically lost.  I wasn't content to simply \emph{lose}, though.  I'd replayed the scene over and over in my head since it had happened, doubly so since I'd found out Coil's power.  If he could create alternate timelines and choose the results, and if he'd used his power to save us, what had happened in that other timeline?  Had we died?



I hated the idea that I owed my life to Coil, because I hated \emph{him}.  I hated that he'd turned something I could almost make peace with -being a villain- and he'd turned it into something that I was deeply ashamed of, something that gnawed at me.  He'd \emph{used }me, and he'd done it to abuse, manipulate and take advantage of a young girl.



That irritation had been one more nudge to get me thinking about how I \emph{could} have handled this.  With every new trick, strategy and technique I came up with, I tended to think about how they could apply to previous encounters, \emph{especially }those encounters where we hadn't come out ahead.



My bugs gave me a way of tracking Night.  I could sense her change as she escaped the line of sight of both her allies and our group.  I didn't hurry after her, but I kept my attention turned in her direction as she transformed into that multi-legged, hyper-agile, lightning quick death blender of blades and claws and moved to flank us.



I called Atlas to me.



So long as I could see her coming, she wouldn't be able to maintain that form as she closed the distance.  That didn't mean her human self was a non-threat.  She was prepared to use any possible method to blind or distract so her opponents would take their eyes off her.  Flashbang grenades, smoke canisters, a cloak that doubled as a net, complete with hooks to catch on costumes and hair.



Fog was in his cloud form, advancing inexorably towards us.  He had the ability to adopt a gaseous body.  He was capable of making the gas semisolid, even maintaining a crude hold on objects.  If someone happened to breathe him in or swallow that smoke, and he made it solid while it was in their bloodstream, it was capable of doing horrific internal damage.



Shatterbird stopped driving the glass shards at our enemies and began collecting the nearby glass instead.  She formed it into a barrier.  The join wasn't perfect, and Regent apparently lacked the fine touch the real Shatterbird had, because he didn't strategically break the glass to make the joints fit better or create smaller pieces to jam in the holes.



Fog was slowed, but not stopped entirely.  He seeped through the cracks.



The high-pitched sound of glass slapping against glass filled the area as Regent patched up the holes by pressing larger pieces of glass over the gaps.  Still imperfect, but it was as good a barrier as we might hope for.



Night had paused.  She'd clearly wanted to use the smoke cover or the distraction of Fog's approach to attack, but with his approach delayed, she was slowed down as well.



I was already prepping my bugs, readying with a response of my own.



I was nervous, I had to admit.  I'd fought against Leviathan, I'd fought the Nine, but Night was never going to be an opponent I could laugh off.



Fog managed to get enough of himself through the glass that he had leverage enough to break it.



``This power is so hard to use,'' Regent complained.  ``So much to focus on.''



``You're doing fine.''



``I'm doing fine because she's \emph{helping.  }I think.''



``Be careful then,'' Tattletale said.  ``Don't rely on her power.''



``Kind of hard not to, unless you want to let him approach?''



Would Shatterbird cease assisting at the most critical juncture, getting us all killed?  It would fit.  Unless she was helping only because she didn't want to die.



``I'm going,'' I told them.  ``Hold down the fort, run if you have to.  We've basically scored a victory here, it's just a question of driving it home.''



I climbed on top of Atlas and flew away from my companions.  If my plan failed, I could fly, but Tattletale and Regent couldn't.  Better that she chase me with the others having a chance to escape than a scenario where I led her straight to them.



My swarm swamped Night, catching her alien, angular legs with strands of silk.



Lots of legs, only so much silk.  It wasn't really working.  It might have been doable if I had a sense of how her body moved, or how the legs bent, but any time I looped silk around what I might consider a knee-joint, it turned inside out, the silk dropping to the ground.



Irritating.



My bugs weren't finding anything I could identify as a sensory organ, no eyes or anything of the like.  Nothing that pepper spray would have an effect on.



Okay.  Something else.  I held back with the bugs that had the silk lines, rearranging them as I closed the distance.



The second I rounded the corner to spot Night, she was human again.  She pulled her cloak around herself, glancing around until she spotted me.



I swallowed, backing away slowly while keeping her in plain view.  My bugs gathered, but not to the extent that they blocked my view of her.



In one fluid motion, she wrapped her cloak around herself and then cast it out so it billowed.  She had a canister in her hand, whipping it in my direction.



I caught it in a net of silk strands buoyed by nearly two thousand flying dragonflies, beetles, wasps, hornets and cockroaches.



Night watched as the canister floated off into the air a distance away.  I readied two more nets, placing them in the air to the right and left.



I knew what she would do next, but that was mainly because I hadn't been able to come up with a good way to deal with it.  I could trust Grue to handle it, but he wasn't here.  I could use my bugs, with some luck, but even then I wasn't sure it would have an effect.



She used a flashbang.



Close my eyes or stare dead on into the flash, I'd be momentarily blind either way.  I opted for the former, covering my eyes and flying both up and away.



With my swarm sense, I could feel her creating some distance, breaking away and heading for the general direction of the others, moving faster than any car, with far more raw mobility, turning on a dime and easily navigating obstacles.  Even before the flashbang went off, I was turning to follow.



I could tell the others were distracted by Fog.  Even some of the other members of the Chosen were slowly pulling themselves together.  I stepped up the assault with my bugs to make up for the fact that Regent and Shatterbird were otherwise occupied.



That left me to catch Night.  She was taking the long way, favoring alleys and going through the ground floor of buildings, which simultaneously let her maintain her monstrous form while forcing her to take just long enough that I could keep up.  The fastest path between two points was a straight line, so I had that advantage at least.



So long as I had eyes on her, I could slow her down, keep her from assaulting my teammates.  If I could catch her in human form, I might be able to bind her, or at least keep those flashbangs webbed to her belt.



There \emph{was} the worst case scenario that she'd get close enough to kill someone in the span that a flashbang blinded us-  I wasn't oblivious to that.



I was gaining on her, slowly but surely.  My heart pounded in my chest as I sensed her closing the gap between herself and the others, my eyes and my bugs scanning the surroundings so I could calculate the best position.  It wouldn't matter how close I got to Night if there was a building blocking my view of her.



She stopped.



Or, more appropriately, she shifted gears from zig-zagging from one piece of cover to another to running at human speed.



I caught up a few seconds later, stopping Atlas so we circled directly above her.



She glanced around, looked up at me, then bolted for a restaurant with a tattered canopy over what had been an outdoor patio.



She disappeared from my sight for an instant, but she didn't change.



The smoke canisters came out, but my bugs had lagged behind.  Anticipating another rush for my teammates, I piloted Atlas to a position between Night and the others.



The smoke spilled out around her, but again, she didn't change.



She collapsed to the ground.



Wary of a feint, I approached with care.



Imp stood over Night, holding a taser.



``Got her,'' she said, ``Fuck yes.  You can't tell me that wasn't awesome.''



``Good job.  Now don't take your eyes off her.  She heals back to pristine condition the second you blink.''



``We take turns blinking?''  She asked.



``Sure.  Blink on five.  One, two, three, four, five\ldots'' I said.  I waited until the second count and started blinking on three.



We draped Night across Atlas and hurried back toward the others, continuing the count.



Shatterbird had Fog trapped in a box of glass, layers upon layers.  Every time a puff of smoke escaped, a layering of glass shards covered the gap.  My allies were all standing, and our enemies were soundly defeated.  After a quick exchange to ensure we were sharing the duties of watching Night, I freed myself to check the scene with my eyes, rather than my swarm-sense.



Rune was kneeling, bleeding from shallow cuts across her face, chest, ribs, stomach and thighs.  She was using her power on a scarf to bind the wounds tight.



Othala was standing off to one side, hurt as well.  Victor was bound.



None of them were meeting our gaze.  We'd won to the extent that it was embarrassing to them.



``You're in our territory,'' Tattletale told them.  ``Get out.''



``You've taken this whole fucking city as your territory,'' Rune retorted, scowling.



``Your point being?'' Regent asked.



``Where are we supposed to go?''



``Leave the city, retard.''  Imp said.



``You can't just take the whole city.''



I didn't feel like Imp and Regent were giving the impression of strength.  I spoke before they could.  ``We already have.  We fought the Nine and played a pretty big part in taking out more than half of them.''  I pointed at Shatterbird, ``Case in point.  You took advantage of that to try to claim some territory for yourselves.  Not only is that awfully pathetic, but you proved yourselves hypocrites, doing exactly what Hookwolf accused us of doing.''



``We staked out our claim.  It's our right.''



``Your \emph{right?}  On what grounds?  Strength?  We have you beat there.  Did you earn it?  No.  I think my team has you beat on both points.''



``Now,'' Tattletale stepped forward, ``Here's the thing.  We can't let you get away with this unscathed.  So we're taxing you.''



``Tax?''  Othala asked.



``Tax.  Imp and I are going to step into the basement of that building over there,'' Tattletale pointed, ``And relieve you of every valuable we can carry.''



``You assholes!'' Rune growled.  She started to stand, then fell to the ground, hard.  Imp had pushed her.  I tried to hide my own surprise at the girl's sudden appearance.  The others looked somewhat intimidated as well.



``But that's not enough, is it?  So there's another tax.  We're borrowing one of your teammates.''



The Chosen weren't the only ones who looked shocked at the declaration.  I snapped my head around to look at Regent.  There was no surprise there.



Fuck them.  They'd planned this, and they hadn't told me.





