





``To use a clich\'{e}, you can do this the easy way or the hard way,'' Tattletale said, a light smile on her face.



``Fuck you,'' Othala snarled.



Tattletale hadn't told me.  I could understand if \emph{Regent} didn't inform me that they were hoping to enslave someone else, but I counted Tattletale among my few real friends.  I had something of a sore spot when it came to being betrayed by friends.



They'd planned to do this at some point today, and I hadn't been filled in.  Was that accidental?  We'd exchanged so many calls, I could almost believe that I'd been forgotten, or that everyone had assumed someone else would be the one to fill me in.



But I couldn't shake the other possibility.  They could have left me in the dark because they knew I'd object.  And now that I was filled in on this plan, I couldn't object without making the group look weak.  Tattletale would\emph{ know }that.  She would know I wouldn't screw us over, even with my objections, and this next part of the plan would go ahead whether or not I agreed or not.



Biting my tongue, I walked around until I stood at the very back of the scene, where I could see Night as well as everyone else that was present.



``Victor,'' Tattletale said.  ``You're the tax payment, so to speak.  Your call.''



Victor's eyes narrowed.



``Consider it an opportunity.  You're bound to pick up \emph{something} you can use, talent-wise.''



``I won't betray my team.''



Regent chuckled, not raising his eyes from Night.  ``Not really getting a choice.''



``The PRT trains its squads in resisting and reacting to master-category attacks.  I've picked up some things,'' Victor's chin raised a fraction.



Victor had a kind of easy arrogance to him.  It wasn't just the arrogance of someone who thought they were better than everyone around them.  It was the arrogance of someone who'd been born and raised thinking they were better, only to have that confidence reinforced and enhanced over the course of their lives.



Even bound by the spider silk, he managed to carry the demeanor of a prince from one of the monarchies of old, transported to the modern era.  He had the look, too: a cleft chin, close-cropped hair that had been bleached to a platinum blond and a stare that managed to look simultaneously condescending and angry.  He \emph{would be} angry, obviously, but I'd seen him in situations where he wasn't trussed up and lying on the ground, and he'd looked the same then.  His costume reinforced the image of someone between eras, with a simple black-painted breastplate with a sharp stylized `v' around the neck, a blood-red shirt and black slacks.



The color scheme extended to Othala, who wore something decidedly more traditional as superhero costumes went.  Her bodysuit was skintight and tomato red, with a single icon in the center. Like the swastika, it featured a circle with a black border and white center, and a rune in black.  It wasn't a swastika, though, but a diamond with two legs extending from the bottom point, each turning up at the bottom.  She'd taken to wearing an eyepatch with the same icon on it in white.  Her hair covered enough of that side of her face that it wasn't obvious.



She couldn't heal herself, of course.  She granted powers to \emph{others}.  There would be no other reason for her to be kneeling in the water, bleeding from a hundred papercut-thin lacerations.



Rune, for her part, wasn't much older than Imp.  Her long blond hair streamed out of a pointed hood, and runes lined the edges of a long, dark blue cloak.



``I'm kind of hoping you're right,'' Regent shrugged, ``Nobody's ever resisted before.  I could learn a lot.''



Tattletale asked, ``Seriously, are you going to cooperate?''



``No,'' Victor replied.  He rolled onto his back and set his head down so he was staring up at the sky.



``Fine.  Imp?''



I turned and saw Tattletale pointing toward Othala.



Imp was there, behind the villainess.  Imp planted one foot between Othala's shoulders and kicked the girl face first into the street



``Hey!''  Victor shouted.  ``Don't touch her!''



``Anything we do to you or Rune, you'll always know in the back of your mind that Othala  could heal it,'' Tattletale said.  ``But anything we do to \emph{her}\ldots''



Imp took that as a cue, kicking Othala in the gut.



``Your issue is with me!''



Tattletale was as calm as he was angry.  ``You're surprisingly upset.  You'd think you'd be used to seeing your teammate taking some lumps in the course of your supervillain careers.  You two are involved, aren't you?  Makes sense, given how closely you've worked together.''



``You don't know the littlest thing about where we come from,'' Victor snarled.



``I'm figuring it out.  Give me a second.  Judging by what you're saying, there's a loss in there somewhere.  Group like yours, bound to be pretty insular.  Making friends with similar beliefs, dating people with similar beliefs.  Did your daddy give you some strong encouragement to date this little lady?''



Victor looked away, his lips twisting into an expression I couldn't interpret.  He shook his head.



``Not quite, huh?  It wasn't your dad.  You were on your own, a lost soul recruited by a big, \emph{proud }family.  Proved yourself, and you were told you'd earn a proper place in Kaiser's Empire if you married in, so to speak.  Not an arranged marriage in the strictest sense, but the idea was that you'd date one of the lieutenant's girls and marry eventually.  Except it wasn't her you were supposed to date.  Her sister?''



``Cousin,'' Victor spat the word, ``I'm getting tired of hearing you fumble your way to answers.  It was her cousin.''



``There we go.  Something happened to the cousin.  So you two got paired together instead.  And you two work so well together, it's a kind of kismet.  Only there's a little heartbreak on both sides.''



``\emph{This} is your plan?'' Victor sneered.  ``Hate to break it to you, but we've talked this shit out.  It's called communication.  You won't be revealing any big secrets to break us up.''



``No.  You two are totally honest with each other.  Kudos.  Thing is, you're just not very honest with yourselves.  You know why you're getting so angry at Othala getting hurt?  You're really quite insecure in your attachment to her.''



``Oh god, this is lame.''  The water rippled as Victor let his head drop down to rest on the flooded street.



``You're playing up your own anger because you're afraid that if you don't \emph{make} yourself care, you won't care at all.''



``Okay, sure.''



``You tell yourself you're growing to love her, but you're a very good liar, Victor, and you're very good at lying to \emph{yourself}.  You know that, so you've found yourself wondering if maybe the feelings you have for Othala are just the head games you've been playing with yourself.''



``Easily possible.  But there's two other possibilities.  It could be that I'm \emph{not} lying to myself.  Let's not forget that.  Another possibility is that it really is just me lying to myself, but that lie will become truth over time.  People all over this city feign confidence, and that becomes something concrete.  You can become the mask you wear on a day-to-day basis.''



Something about that bothered me.  I spoke for the first time since Tattletale had declared her intentions.  ``Seems kind of hollow.''



``Because it's not a fairytale romance?  It's not.  But I'll tell you I enjoy her company, I trust her, I respect her, and I'm even attracted to her.  We've got a foundation, bug girl.  There's nothing \emph{forcing} us to stay together anymore.  Empire Eighty-Eight is gone.  We're a pair because we want to be.  Right, O?''



``Right,'' Othala's voice was quiet.  She'd pulled herself up onto her hands and knees.  She glared up at Imp, then looked down.



Tattletale stepped forward, ``Or because your names and faces are known to the public, and instead of being part of your group by choice, you're part of the group because nobody else will have you?''



Victor laughed a little.  ``Somehow I expected better from you, Tattletale.  This is pretty feeble.  Attacking our relationship?  We're strong enough, and no matter what you try to pull, you won't change the fact that we have what it takes.''



``Sure.  But I don't have to.  Your relationship is doomed.  You don't have that same lovesick, infatuated feeling for Othala that you had for her cousin.  The chance for that moment has passed.  And it'll eat away at you.  You'll crave that kind of feeling, and feel like you missed out on something by throwing yourself into a relationship out of \emph{duty} rather than love.  You'll cheat because you're searching for that and because it's \emph{easy }for you to get women.  You're good-looking, and you have access to all the little tricks, how to approach them, how to win them over.  And Othala over there, she's still head over heels for you.  It'll kill her when you betray her.''



The smile slipped from Victor's face.  ``You're not saying all this to fuck with me.  You're fucking with \emph{her}.''



I glanced at Othala, who was staring down at the ground.



``Why?'' he asked.  ``Why do this?''



``What other options do we have, if we want to pressure you?  You're invincible for at least a little while longer, but even without that, if we beat and tortured you, I think we'd come out behind, just by virtue of how far we'd have to go before we got past whatever interrogation resistance techniques you've stolen.  Wouldn't be much different if we beat and tortured \emph{Othala}.  We'd piss you off, but I don't think we'd break you.  So at the very least, this is a more civilized route of attack.''



``You don't need my agreement, and I'm not about to give it.  Not betraying my teammates.''



``Your agreement would make all of this a lot easier.  Don't play dumb and say we don't need it.  You and I both know you're a master of martial arts that you could use if we cut your legs free.  Capoeira, I imagine.  There's certainly others you could draw on, and I'd bet you've blended all those styles together.  You'd kick our faces in, maybe distract us long enough for Night to bounce back.''



Victor smirked.



``Regent and Skitter would stop you without a problem, but that's a lose-lose situation.  You and your buddies end up dead or seriously injured, and we don't get to borrow your talents.  But you'd do it, to deny us what we want and because you hate it when someone else comes out on top.''



``And what makes you think you're going to change my mind?''



``The fact that that was just a sampler.  I'm just getting started.  We're not in any particular rush, so we can sit here until I've completely fucked up your group.  I'll find every little chink and weak link there is and leverage them until you break,'' Tattletale shrugged.  ``You think on that while we go take our pick of your stuff.  There's bound to be some juicy clues in your living space.  Imp, come on.''



Tattletale and Imp headed off to collect the spoils.  I settled down, silently fuming, keeping one eye on Night.



Silence lingered for a good minute.



``You can cheat,'' Othala said.



``Not now, O.''



``We open up the relationship.  You do what you need to, just promise that if you don't find what you're looking for, you come back.''



I spoke up, ``Not sure if it's really true, given who you're associating with, but don't you deserve better than that?''



``Shut your mouth-hole, heeb,'' Othala snarled.  ``Butt out.''



I felt my heart skip a beat at the `heeb'.  She knew my last name?



No.  Heeb was short for Hebrew, not Hebert.



\emph{I'm not Jewish,} I thought.  How had she come to that conclusion?  I could believe someone would make an assumption like that if they'd seen my skin tone and hair, but my costume covered my skin.  I'd spent some time wearing a mask that \emph{did} show some skin, after Bonesaw had cut up my good mask, but Othala hadn't been there for any of those incidents.



I had ideas about what that could mean, but I kept my mouth shut.



``Don't stress about it,'' Victor said.  ``She's trying to get to you.''



``No shit,'' Regent muttered.



``I'm just thinking if we can find a solution to this, then I can be more confident we'll find solutions to the other stuff.''



Victor shook his head.  ``Just relax.  There's no rush.  Any problem Tattletale brings up, every issue, it's something we can work through.  If you get panicked, if she starts making you think that whatever she's talking about is suddenly a \emph{crisis} and it has to be addressed \emph{right now}, you're playing into her hands.  She'll use that to make you say or do something you'll regret.  So take--''



``Regent, keep an eye on Night?''  I spoke, interrupting.



``Sure.''



Victor stared at me as I approached.  I held out one hand and let a spider drop from each fingertip, dangling from threads.



``The hell?'' He squirmed in an attempt to get away, but his arms and legs didn't afford him much room to move. I slowed their descent enough that he could see the spiders clearly.  Black, orblike abdomens, stamped with a red hourglass marking.  If it wasn't for my wanting to do this to make it clear what spiders they were, I would have just used the spiders I'd employed to wrap him in silk.  I wanted the drama and to make it absolutely clear what I was doing.



I moved my hand and let the spiders swing a little to the left to make sure they were in place and let them settle on his face.



``Hush,'' I told him.  ``Now close your eyes.  You don't want to startle them or they'll bite.''



One of his eyes fluttered in a reflexive action as the spider touched his eyelash.  He growled ``You psycho,'' scowling, before shutting his eyes.



I moved more spiders into positions on his lips.



``Careful,'' I said.  ``I'm focusing on watching Night, so I'm not really bothering to suppress their instincts.  Don't move.''



I looked at Rune and Othala, ``You two be quiet, too.  I can handle you the same way.''



Othala only stared, while Rune offered a slow nod.



It took five more minutes for Imp and Tattletale to come back, each loaded down with bags.  Given the variety of labels, I guessed the bags contained things looted from stores downtown.  Imp put down a spray can, and set to spraying the glass cube Shatterbird had imprisoned Fog in.  Filling in the gaps, cementing it together.



``I'd step back, Skitter,'' Tattletale said.  ``His power works by proximity, among other things.  Physical contact, eye contact and active use of a skill lets him leech them off you.  The stronger the contact with each transfer point, the more transfer points he's maintaining, the faster the drain.  He could suck away something essential, or make you just a \emph{little bit} worse at everything you do.''



I stepped away, silent.



``So, have you made a decision?'' Tattletale asked Victor.  ``Because I'm all geared up to carry on with the discussion here.''



Victor didn't respond.  Couldn't.



Tattletale turned to look my way, and I met her eyes.  I left the bugs in place.



``Could you please move the spiders?''  She asked.



``Of course.''  I dismissed them, but I didn't break eye contact.



She was the first to look away, turning her attention to Victor.  ``Well, Victor?''



He looked over at Othala, then stared up at Tattletale.  He managed to look confident despite being bound and lying in the floodwater.  After a long moment, he said, ``I'm undecided.''



``That's a step forward,'' she said.



``Maybe you could provide me some incentive?''



\emph{He needs to win on some level if he's going to make a concession}, I thought.



Regent shrugged.  ``I could keep you for seventy-two hours, if you don't cooperate, or thirty-six if you do.''



Victor turned to look at Regent.  ``That'll do.''



``Can you cut him free?''



I had my spiders start severing the threads.



``You leave the others alone,'' Victor said.



``Skitter will keep an eye on them until we're a safe distance away, and then she'll give them the signal that it's okay to move,'' Tattletale said.



I nodded.  I didn't \emph{agree}, but I would play along for the sake of the group's image, and because I wasn't willing to sabotage a plan in progress, even if I didn't agree with it.



I brought Atlas to me and was in the air a few seconds later.



Between Imp and I, there was a pretty slim chance that we'd both blink at the same time and leave Night free to use her power.



When Tattletale and Regent were out of my range, I turned to leave.  Night didn't turn into a monster, but I took that to be a result of her being unconscious.  Or maybe the taser's effects.  Either way, I wasn't complaining.  It gave me more of a head start.  When the Chosen were at the limits of my power's range, I drew words in the air to let them know it was safe to move.



I caught up with the others a short distance away from Regent's headquarters.  Victor was being loaded into a van, hooded and heavily shackled.  Another truck was parked a short distance away.



The moment the door was shut, I stabbed one finger in Tattletale's direction, ``What the \emph{fuck} was that?''



``Woah,'' Regent said, ``Relax.''



``I'm not going to `relax'.  You two \emph{deliberately} left me in the dark, there.  Or it was an exceedingly \emph{stupid} oversight to forget to mention it, and I know Tattletale isn't stupid.''



``It was only sort of deliberate.  Regent didn't have any part in that.''



``Explain,'' I told her.



``I didn't realize you had such an issue with Regent using his power until you brought it up before.  I could have mentioned our secondary goal then, but I was worried that would start something.  Or that it would discombobulate you before we got into a thing with the Chosen.''



``As opposed to finding it out \emph{right after.}''



``I'm sorry.  Again, I really underestimated how much you'd care.''



``I was okay with Shadow Stalker because she's a legit psychopath, and sure, there was some personal bias in there.  Whatever.  I'm also cool with Shatterbird because I don't think there's a shred of humanity in there.  This is different.''



``See, that's what throws me,'' Tattletale said.  ``I don't see that big a difference between Victor and Shadow Stalker.''



``I've spent more than enough time around Shadow Stalker to feel confident in making the call.  I haven't spent any time around Victor.  I didn't know if he's a psychopath, if he's just deluded, or if he's being forced into what he's doing.''



``I could have filled you in.''



``You're right,'' I said, ``You \emph{could} have.  That's all I wanted.  I just wanted you to ask.''



She frowned.



``And, of course, now we're locked into this thing, and I can't help but wonder if I can trust you in the future.''



``That's rich,'' Regent said, ``Coming from you.''



I shook my head.  ``I've played along.''



``Bullshit.  You've demanded concessions and compromises from us every step along the way.''



``And I've made concessions and compromises.  I accepted it when you revealed your \emph{real} power, I agreed we should capture Shadow Stalker for the one job.''



``Let's call a duck a duck.  You agreed to capturing Shadow Stalker because you wanted revenge.''



I shook my head.  ``No.  Remember when I first brought up the bullying?  I was pretty clear about how I didn't want any of that.''



``You \emph{said} it, but that's a long ways away from meaning it.''



``I say what I mean.''



``Says the most dishonest members of the group,'' he retorted.  Before I could reply, he raised both hands, as if to ward me off.  ``Not really intending to get on your case, not accusing or insulting you.  Just saying: the whole undercover operative thing, I don't think you have much ground to stand on.''



I looked away.  ``I'm not proud of that.''



``Sure.  That's fine.  But let's be honest about all this.  You spent a whole lot of time saying one thing while doing another.  I think we all rolled with that pretty damn well.  Even went the extra mile on some occasions.  Well, Rachel excepted, but yeah.  Are you saying you can't return the favor?''



``If we're talking mind control--''



``No,'' Tattletale cut in.  ``We're not.  We've already established a precedent when it comes to using Regent's powers on the legitimately fucked up.  And I already knew Victor fit that label.  \emph{Your} issue is with my neglecting to fill you in.  I'm willing to admit I was wrong.  It was a bad call on my part, to leave you in the dark.  It's \emph{your} call if you want to accept that apology and move on.''



``And how often can this happen before I can say we're taking it too far?  Regent's power is going to get us in trouble, one way or another.  If our enemies decide that the threat of being mind-controlled is too big, and band together against us, it might be creating more of a disadvantage than an advantage.''



``It's body-control, not mind-control,'' Regent said.  ``I don't touch the grey matter.''



``Semantics.  My point stands.''



``Then let me raise my own point,'' he said.  ``What am I supposed to do, if I'm not using my power?  The whole bit with tripping people up, knocking them down, making them drop shit?  It's not exactly grade A material as superpowers go.''



``I'm saying we \emph{discuss} it as a group before enslaving someone.''



``And if there's a window of opportunity?'' he asked.  ``A chance to capture someone on the fly?  Do we just let it slip by because you want to host a debate?''



``No,'' I sighed.  ``You could capture the person in question, we hold them for long enough to talk it over, then we let them go if it isn't appropriate.''



He shrugged.  ``Which doesn't do a damn thing to ease people's suspicions if everyone's watching their friends, seeing if anyone's dropped off the map long enough to have been captured and converted.  I've been there.  Maybe not on this scale, but I've seen it happen, the paranoia.''



``Right.  And your little plan here has started that ball rolling.  Whatever we do from here on out, people are going to be spooked enough that they'll see the mind controlled where they don't exist.''



``Fear is good,'' Tattletale said.



``Paranoia isn't.  If our enemies are backed into a corner, they might do something stupid.  You yourself said how Victor was willing to attack us if we cut him free, even if it put himself and his teammates in grave danger.  And he's not dumb.''



``He's not brilliant either,'' Regent said.  ``Just saying, but having a power that gives you brains doesn't necessarily mean you're \emph{smart}.''



Tattletale gave him an annoyed look, then turned to me.  ``I can understand your frustration.  You feel like we just set ourselves back on a city-wide scale for a relatively minor gain.''



I shrugged, ``Pretty much.''



``Except our enemies are already banding together to attack us.  Having Regent as a target doesn't change anything except taking the focus off of more important members of the team,'' she said.



``I see what you did there.  A little quid pro quo,'' Regent muttered.



Tattletale stuck out her tongue at him, then turned back to me, ``And people are going to be scared to take him out if it means releasing Shatterbird.  Picture yourself in their shoes.  It's not a comfortable position to be in if you're itching to retaliate.''



``It's not a comfortable position to be in anyways, even with him on the team,'' I said, glancing over at Shatterbird.  Not that we hadn't taken countermeasures, but\ldots yeah.



Tattletale looked as well.  ``But the main thing I was getting at is that we're working towards something here.  We got Victor.  Bully for us.  But you're probably wondering \emph{why}.''



``Just a little.''



``Remember our attack on the PRT headquarters?  We walked away with data.  Data Coil and his best people couldn't crack.''



I nodded.



``I think Victor could pull it off.''



``Okay.  Still not convinced.''



``Hear me out.  I told Coil that, and that got his attention.  I had \emph{something} of an idea that Victor, Rune and Othala were looking to leave the Chosen, so I floated the idea to Coil that he could make them an offer.''



``I'm not so sure I'm a big fan of that idea.''



``I don't think they'll accept.  But if they do, I think it'll work out for us anyways.  But I'm getting off topic.  The important thing isn't recruiting them, but letting them know in a roundabout way that we're involved with Coil and Coil's involved with us.''



I nodded.  Outing Coil and his relationship to our takeover, maybe possibly.  There were advantages to that.  It would divert attention from us and maybe distract him.



``Point three.  Just a theory, but what if Grue could borrow Victor's power and get some permanent boosts?''



``Just as an idea?  It's interesting.  You brought this up with him?''



``No.  Imp said he was resting when I called to ask.  I figure it can't hurt.''



I nodded.



``So we're getting the data, we're possibly outing Coil, and we're putting a skill vampire in a situation where he's surrounded with some \emph{very} skilled people.  Like a kid in a candy shop, I doubt he'll be able to keep from drooling.  Coil won't let Victor get in situation where he can pick up anything special unless he agrees to join, that's obvious enough.  Except I've talked to Minor, Senegal, Pritt and Jaw, and they're willing to give him a little something in the way of exclusive skills he wouldn't otherwise have access to, in exchange for a few small favors.''



``Like?''



``Like getting a read on Coil's talents and skills, perhaps.  I can't say for sure, but I'm thinking Victor could tell us what Coil's day job used to be.  Enough of a starting point that I can dig up more details.  \emph{Know your enemy}.  And with a guy that versatile, I can think of several ways he could be useful.''



``Okay,'' I said.



``Okay?''  She asked.



``Okay.  Yeah.  I wish we could have talked about this before, but I'm willing to accept that we've been through a hell of a lot, and you've put up with a lot of demands from me.  If you think this is a good idea, if you're certain about this, I can accept that.''



She nodded once, ``Thank you.''



``And me?'' Regent asked.  ``No `I have faith in your judgement'?''



``I really don't,'' I admitted.



``Pshh.  After everything I've done for you.''



``Hm?''



``Nevermind,'' he said, chuckling.  ``I'm going to catch a ride to Coil's and handle this next bit.  Wonder how long he'll hold out.''



``I'll come too,'' Tattletale said.  ``I want to see how this plays out.''



``If you don't need me, I'm thinking I'm going to head back,'' I said.  ``Take care of my people.''



Tattletale nodded and gave me a short wave as she climbed into the back of the second truck.



I wasn't \emph{thrilled}, but I could deal.  I felt relieved to have a window of time to do what I needed to do.  It wouldn't be relaxation, but more moving on to the next point on my priority list, handling the stuff that absolutely positively needed to be handled.  Making sure my dad was protected from Coil was a big one, making sure my people were both protected and equipped to protect themselves from the Chosen was another.  I needed to get my equipment in order, and the costumes finished, make sure I touched base with Bitch so our recent good relationship didn't fall apart, and maintain the lines of communication with Tattletale and Coil so I was up to date on upcoming events.



``Do me a favor?''  Someone asked from behind me.



I spun around, drawing my knife.  It was just Imp.  Damn it.



``What?'' I asked.  ``Where'd you come from?''



``I stayed behind to keep an eye on Night.  Winking instead of blinking so I didn't lose sight of her.  And you don't even remember that I was doing it.  Fuck.  Ungrateful bastards.  I had to run the last block so I could be sure you didn't fly off before I could ask.''



``You could have phoned.''



She shook her head.  ``You heard what Tattletale said.  Coil might be listening in over the phones.  We don't mention anything we wouldn't want him to overhear.''



``And you don't want him to overhear this favor?'' I asked, hating myself even as I opened my mouth.



How was I supposed to get a handle on everything if I was posed with two more crises every time I got something done?





