





Sundancer had once described her life in costume as intense, violent and lonely.  I'd had a hard time understanding the last point.  That had been about the same time that I had been riding the high of having friends for the first time, after a couple of years spent in almost total solitude.



Maybe, if the subject had come up again in recent weeks, I might have understood, nodding my head in sympathy.



Powers raised us above the common people.  It was maybe arrogant to think that way, to say I was better than the likes of Sierra, Charlotte or my father, but I sort of \emph{was}.  I had all the potential they did and then \emph{more}.



Even if I looked at how powers elevated us, though, I had to admit we weren't raised to the same level.  We weren't all raised up \emph{together}.  If anything, the powers drove us apart: our trigger events, our reasons for wanting to use our powers, the agendas and missions we took upon ourselves, and even how those powers made us think and operate in different ways\ldots they put barriers between ourselves and others.  I just had to think of Panacea or Bitch, and I had some damn good examples of that.



I couldn't think of two capes who were in a committed relationship where there wasn't some degree of fucked-up-ness.  Night and Fog were, if I'd understood Tattletale right, essentially functional sociopaths.  They'd acted out the role of a married couple with none of the affection or fondness.  Victor and Othala were screwed up in a different way, burdened by a shared event in their past.  Brandish and Flashbang?  If their kids were any indication\ldots yeah.  Fucked up.



It was no small wonder we were all so fucked up.  It was the human condition, to need a supporting hand now and again, and yet we could barely help ourselves, let alone each other.



Worse, if by some small miracle two capes managed to find comfort and support in each other, there was no guarantee that those other two points that Sundancer had raised wouldn't ruin things.  The intensity of our lifestyle and the sheer violence.  Lady Photon had lost her husband in the Leviathan fight.  Glory Girl had, if the magazines and papers were any indication, maintained an on-and-off relationship with Gallant.  He'd died too.



So this?  Lying here beside Brian?  It was sort of bittersweet, with maybe a 60-40 split on the sweet vs. the bitter.



I couldn't see Brian's face without raising my head, and I didn't want to do that and risk waking him.  I'd left my glasses on the table with the knife and gun, so I couldn't see that well anyways.  I settled for studying the fabric of his sleeveless shirt, the nubs of lint, the weave of the textile, and how it shifted with the slow, deep and rhythmic breaths he was taking.  I could smell his sweat, with the faint traces of his deodorant beneath.  It was funny, because when we'd settled in, I hadn't been able to smell anything.



I felt warm in the core of my chest.  That wasn't just the morning light streaming in through the windows.



Not happy, exactly.  I didn't feel like I deserved to be happy, not with the responsibilities I wasn't attending to right now, not with the mistakes I'd made and the people I'd failed.



But I could convince myself that this was something I should be doing.  It was one of the tasks that I had to tend to, no matter how the coming days and weeks unfolded, and we'd settled on making those tasks a priority.  We had to support Grue if we wanted him around to help us when everything started going down.



I wouldn't rest any hopes on this, not with the way every other parahuman relationship seemed to go.  I'd take these individual moments for what they were.



All of which amounted to a pile of excuses and rationalizations I was layering on top of one another, trying to convince myself this wouldn't end disastrously, that I wasn't being irresponsible or that I wasn't going to regret this on a hundred different levels.  It was enough that I could feel at peace, here.



\emph{Mostly} at peace.  I had to pee, and yet I didn't want to move and disturb him.



Nothing was easy, it seemed.



My body won out over my willpower, and I decided to extricate myself.  I didn't even try to get to my feet, instead easing myself down to the ground as I unwrapped myself from Brian as slowly as I could.



Once I'd disentangled myself from Brian and the couch, I grabbed my glasses, knife, cellphone and gun and rushed to the washroom.



The cell phone rang while I was on the toilet.  Tattletale.  For Brian's sake and my own sense of decency, I refused the call and texted her instead:



What's up?



She replied soon after:



R is done.  Bird in the pen 4 now.  C wants a meeting neways.  Get G I and come 4 11am?



So it was time to see if Brian could glean anything from Victor's power.  I responded:



G sleeping.  Don't want to wake him.



I could guess her reply before it appeared:



hate to break u 2 lovebirds up but we r tight on time and C is impatient



I texted her an a-ok before hanging up and putting the phone away.



The kitchen had been cleaned up, but my bugs hadn't alerted me to anyone coming in.  Had Aisha returned and used her power to stay quiet?



I decided to assume she had and began preparing breakfast for three people.



If I had to rouse Brian, I'd do it with the smells of bacon, coffee and toast.  It was as inoffensive a method as I could think of.



Aisha woke up before Brian did, venturing downstairs in a long t-shirt.



``Thanks for cleaning up,'' I said, quiet.  I could remember her reaction the last time I'd been talking to Brian, and added, ``And for not getting upset.''



``I can't help him, don't know how.  So I'm putting it in your hands.''



``Thanks.''



``Don't thank me.  If you screw this up, I can and will make your life a living hell.''



I frowned.  ``Honestly?  That's not very fair.  I think I probably will screw up along the way.  This isn't going to be smooth sailing, whatever happens.  So maybe it'd be better if you just trust that I'm going into this with the best intentions for him.''



She plucked a piece of bacon from a plate and popped it into her mouth.  ``Maybe.  But no. Don't fuck this up.''



I rolled my eyes.



``I've had a lot of practice.  It's the little things, convincing someone they're going crazy, nothing they put down is where they left it.  Things go missing.  Furniture gets moved.  Then it gets more serious, they find the stash of drugs they were supposed to barter for stuff is missing-''



``I don't have any drugs,'' I told her.



``Talking hy-po-theticals.  I get them in trouble with people they know.  Then they have little injures they can't remember getting.  Splinters under their fingernails, papercuts between their fingers or at the corners of their mouths, little cuts on the back of their hands.  That's usually when they freak out.  They run, go somewhere else, and it stops, just a little while.  Until it comes again, twice as bad as before.  They snap.  Then I leave them a message telling them that it all stops when they leave the city.  Put it on their walls in blood or put it on their bathroom mirror in soap so it shows up when the room gets all steamy.  They're \emph{glad}.  They're happy to have a way out.  Except I wouldn't leave you that note.''



``What the hell are you talking about?'' Brian asked, from behind her.  ``And where are you getting that blood?''



Aisha wheeled around, not appearing even half as guilty as she should have.



``I asked Coil's lieutenant for some.  He asked me how many gallons I wanted.  How weird is that?  I mean, seriously, who needs \emph{gallons} of blood?  Or maybe I \emph{could} use it.  Paint someone's house, see if I can't freak them out hardcore,'' Aisha smiled wickedly.



``Ignore that question.  What were you saying to Taylor, about not giving her a note?''



``It's fine,'' I told him.  ``She's being protective of her big brother.''



Aisha plastered a fake smile on her face.



``I didn't know you cared,'' Brian told Aisha, with a touch of sarcasm.  ``I'm dropping this only because Taylor's sticking up for you.''



Aisha rolled her eyes and began serving herself.



It was nine-thirty.  Assuming it would take us half an hour to forty-five minutes to get to Coil's place, that left us only about an hour to get ready.  We ate in awkward silence.  Aisha took the first turn in the shower, leaving Brian and me alone once again.



I didn't know what to do with myself.  We had taken a step forward, but I didn't exactly have any experience on this front.  What was I supposed to do?  What did I say?  I wanted to hug him, to hold his hand or raise the idea of spending time together later, but I didn't know what was allowed, or what would be pushing boundaries or taking things too far.



He sat down on the couch, putting his feet up on the coffee table, and I grabbed a glass of orange juice before sitting down next to him.  Would he put his arm around me, or-



``This thing with Coil.  Do you have a plan?''



Opportunity missed.



I shook my head.  ``More like I have a bunch of smaller plans.  Can't commit to anything, in case things unfold in an unexpected way.''



``Okay.  Let's talk about them.  Plan A?''



``I whip my territory into shape, Coil decides that it's more valuable to keep me in his service.  The idea is that he values my ability to keep an area stable more than he values having Dinah.  He lets her go.''



``Not likely.''



I frowned.  ``I almost gave up on it after Burnscar torched everything.  It isn't \emph{that} impossible.''



``Think about what it would mean in terms of security leaks.  If he let Dinah go home to her family, she wouldn't be able to return to her normal life.  If Coil was dumb enough to let her go with no safeguards and without people to watch her, then the heroes would swoop in on her and use her to get him.''



I nodded, glum.



``And really, can you honestly say that your services are worth the cost of everything you're taking from Coil in the way of resources, \emph{plus} the cost of the agents he'd need watching Dinah at all hours?''



``So you think he'll say no.''



``Tattletale thinks that Coil may be considering dropping you from the team once he has what he needs.''



I turned to look at Brian.  His forehead was creased in a frown.



``You think I'm expendable.''



``To Coil?  Possibly.''



I nodded.



``It's something to keep in mind,'' he said.



``Thing is, I don't know how that really changes anything.  Should I stop helping the people in my territory?  I'm not going to.  It wouldn't be fair to them, and it would tip Coil off.''



``I think it was a bad idea to tip him off by making the deal in the first place.  Now he knows you've got pretty strong morals.  On a level, anyways.''



I nodded.  \emph{On a level}.



He went on, ``I imagine it's troublesome to have someone with those sorts of moral concerns that could throw his long-term plan off course.  He might be looking to replace you.''



``And with his power, that might make for a bit of a pinch.''



``His power?''



I paused.  ``Tattletale clued me in.  He creates parallel realities.  Makes two different decisions, and he gets to see the outcome of each as they unfold.  Decides which he wants in the end.''



Brian frowned.  ``And he's been doing that with us?''



``Since before I joined the team.  Send us on a job in one reality, keep us back in another.  If we succeed, great.  If we fail\ldots well, nothing lost.  He deletes the reality where he sent us out.''



He rubbed his chin.  I noticed he had stubble.  ``So he gets two tries at everything.  Including dealing with any of us who cause him any trouble.''



I nodded.  ``Which is why we need to play along for as long as possible.''



``Fair.  What's your plan B?''



``Plan B\ldots well, it's not so much a plan as a fallback.  If I get found out before we make any headway, it means fighting Coil and his underlings.''



``The Travelers and Circus included.''



``Tattletale and I have talked about how we might approach that.  The problem is that Coil would be backing them up.  Normally I'd suggest we go on the offensive, so they don't have time to go after \emph{our} weaknesses, but with Coil at work, we have to assume that it's all the more likely that the Travelers would get that one lucky hit off, or that they'd pick the plan of attack that would work out for them.''



``And they're powerful enough that they'd really only need to get lucky once,'' Brian said.  I saw his expression darken.  He was staring off into space.



``Sorry,'' I said.  Impulsively, I leaned closer, so my arm and shoulder pressed against his arm.



``Hm?''



``If you want to talk about something else-''



``I want to make sure we come out of this alive.''



``But it's stressing you out.''



``I'll manage,'' he answered, putting one arm around my shoulders and hugging me close.



But he didn't raise the subject again.  Aisha got out of the shower, he took the next turn, ostensibly to clean up after her.  I took the brief period of quiet to get my stuff in order.  I'd worn my costume under my clothes, the top and dress portion  bound around my waist, beneath the sweatshirt.



Once I was free to use the shower, I pulled off the costume and hung it up.  The steam would help with any wrinkles for the parts that weren't skintight.



I had to admit to being a little disappointed with the way the morning was unfolding.  Part of that was with myself, not knowing how to act, but part of it was with the lack of romance.  \emph{Rationally}\emph{, }I knew that the movies, TV, books and all that, they didn't paint a realistic picture.  I knew that we wouldn't instantaneously click, that everything would be fixed.



But at the core of it all, I wasn't a hundred percent rational.



Had to take what I could get.  Last night, cuddling?  It had been nice.  Really nice.



All in all, we were ready to move out well ahead of time.



I wracked my brain, trying to think of things to say.  Everything social or romantic seemed forced or awkward, especially with Imp there.  Everything related to our costumed selves seemed too delicate, fraught with reminders for Brian.



Each time I entered Coil's headquarters, it seemed like it had transformed.  On our first visit it had been a bare bones setup with piles upon piles of crates, and soldiers congregating wherever there was room.  Our last visit had seen some organization.  Now it had finally taken form.



The interior was divided into two levels.  The lower level sported a cafeteria, a bar, a small computer lab and bunk beds for the soldiers on standby.  Doorways leading to what I suspected were washrooms.  I knew that Coil had squads positioned across the city by now, in quarters not unlike the lairs he had assigned us, if a little more austere.  Anyone who stayed here had the bare necessities.



There was an area with more of a focus on the actual `war' part of soldiering, with men at the ready to hand out the guns and ammunition that were tidily arranged on racks and shelves, a massive laundry room that appeared to be devoted to washing and preparing the uniforms and two more stations for heavier gear and more esoteric stuff like walkie-talkies and explosives.



The upper level was pretty plain, with a metal walkway bridging the gaps to the doorways that were recessed in the concrete walls.  Still, things had been added, including whiteboards with shift schedules and maps very similar to the one I'd seen in Tattletale's base of operations.



I glanced at one map; our territory had expanded somewhat.  Or maybe it was better to say that the pockets of enemy forces that had lurked at the edges of our territory were collapsing.



Cranston, the blond woman who served as one of Coil's liasons to us, who was \emph{my} contact when I needed something, was standing outside the door to the conference room.



``Skitter.  How are you?''



``I'm fine, Ms. Cranston.''



``You're a bit early.  Can I offer you anything while you wait for Coil to arrive?''



I shook my head.



``Grue?  Imp?''



They refused as well.



``It'll only be a few minutes.''



Grue and Imp stepped away to talk to the fat, short man who I took to be \emph{their} liason.  I stepped over to the railing and watched the scene below.



A group far to my left caught my eye.  I ventured closer.



Trickster, Sundancer, Genesis and Ballistic were gathered around Tattletale, joined by Coil and a blond boy with striking good looks.  I couldn't really get a good look at it from my vantage point, but the wall jutted out beneath the walkway, and there was a heavy vault door set into the concrete, similar to the ones I'd seen at the shelters.



\emph{Noelle}.



Tattletale was shaking her head as she talked.  She gestured toward the door.



I could see the Travelers respond to that.  Trickster folding his arms, Sundancer turning away slightly.  Genesis, in her wheelchair, hung her head just a bit, her mop of hair blocking the view.



They weren't hearing what they wanted to hear.



Tattletale touched the wall, some panel or button system, said something, and then turned away, walking towards the staircase.  The Travelers and Coil followed behind.



``Everything okay?'' I asked Tattletale, as she joined me.



``Oh, not really,'' she gave me a tight smile.



``Fill me in later?''



``Can't.  Sworn to secrecy.''



``Uh huh.  You know, for someone who calls herself Tattletale, you're way too fond of keeping secrets.''



``Believe me, some secrets aren't so fun to keep.''



I frowned.  What was going on there?



I could only trust that she'd inform us when we weren't in earshot of Coil and the Travelers.



Bitch and Regent were waiting outside the conference room as we approached.  I gave Bitch a small nod of acknowledgement, and she returned it.  All together, we got seated; Travelers on one side of the table, Undersiders on the other, Coil at the head.



``I understand that things have been hectic since the Nine departed the city.  Communications are difficult to establish, there's still lasting damage from the Endbringer attack, and everyone has their individual concerns.  Before our focus fell on the Nine and eliminating Jack Slash, I told you to establish your territories and do what you could to effect some sort of control.  As Tattletale may not have all of the necessary information to draw the right conclusions, I'd like each of you to inform us on your progress.''



He gestured to Trickster.



``Putting me on the spot, huh?''  Trickster asked.  ``Dunno.  Nobody's doing business in my neighborhood, and there aren't any crooks there that the public knows about, but Purity and her people are still hanging around, and I'm waiting on my teammates to wrap up their stuff so they can lend me a hand.''



``Infrastructure, recruitment?'' Coil prompted.



``I've made a few small steps forward for each of those things.  I offered some of the low-level thugs the option of moving out of the city or serving under me.  Got a half-and-half split of each, more or less.  Enough people to deal product, if you want, or to scare some people.''



``Good.  Sundancer?''



Sundancer had the posture of someone who'd desperately hoped to avoid being called on in class.  ``I don't know.  I've been working with the maps Tattletale provided me, but I'm not good at this.  I burn them out of whatever place they're holed up in, they run, then half the time it's like they settle somewhere else that's nearby.''



``You have to scare them more,'' Trickster said.



``I burn their houses down.  I don't know why that's not scary enough.''



``You're too soft about it, being too careful to let them know what you're doing and when, because you don't want to hurt them and \emph{they can tell}.''



Coil cleared his throat.  ``How far along?''



Sundancer didn't look happy.  ``I dunno.  I've maybe cleared out one in four of the local groups?''



``Genesis?'' Coil asked.



``Mostly clear,'' Genesis replied, leaning forward and putting her elbows on the table, ``Not sure how to get anything going in the way of operations.  It's not exactly heavily populated territory.''



``You're keeping Noelle company tonight, yes?''



Genesis nodded.



``Then we'll discuss it then.''



``Okay.''



``And Ballistic?''



``Further along than him,'' Ballistic jerked a thumb toward Trickster.  ``Nobody doing business in my area, only two capes hanging around.  Got that girl from Dolltown who's pretty insistent on holding onto her neighborhood, even if pretty much everyone that lived there is dead, now.  It's the only spot that I haven't taken over.''



``I see.  And the second cape?''



``There's a kid from the old Merchants group.  Has powers.  Going to try to scare off the Doll girl and recruit the Merchant kid.''



``You might start with remembering their names,'' Genesis pointed out.



``I'm not a cape geek like you.''



``You're a \emph{cape}.''



``Parian and Scrub?'' I spoke up, hoping to keep them from going off on a tangent.



``Sure.  Sounds right,'' Ballistic conceded.



``If you're dealing with Parian, can I come along?''



``Actually,'' Coil said, ``I had a request to make of you, Skitter.''



I turned my attention to him.



``After,'' he told me.  ``Let me get to the main topic of this meeting before I address it.  For now, I'd like to hear how the Undersiders are coming along.''



``Been busy helping everyone else out,'' Tattletale admitted.  ``Like Trickster, I guess, I'm waiting for others to finish what they're doing.  I'm pretty solid for business, though.  Bringing in more cash than I'm spending.''



``What's the business?''  Trickster asked.



``The big one is reclaiming items and homes.  I offer goodies to any people from the shelter willing to band together and scare them off, anything too difficult, I use the mercenaries you provided.  Coil's hooked me up with some banking services so we can actually make the transactions.  People don't have a lot of use for money with the way things are right now, and they \emph{do} have stuff that they value.  Figure a few hundred to a thousand dollars per job, three or four jobs a day, and they're sort of doing my work for us, dealing with the gang members.''



``With the idea that your teammates will claim the areas at a later date,'' Coil said, his voice firm.



``Right.''



``Grue and Imp?''



I saw Grue hesitate.



``Seventy-five percent clear,'' Imp said.  ``The Chosen and leftover Merchants mainly moved into our territory and Regent's.  Maybe we're not a hundred percent done, but when we scare people off, they stay gone.''



``Good.  Can you drive out the remaining threats in the next two days?''



``Got this far in three, don't see why not.''



``Excellent.  Regent?''



``About the same.  Nobody wants to cross Shatterbird, but lots of people keep popping up, moving in because they're oblivious that she's there.  With no radio or TV, they're clueless.''



``Make it more obvious, then.''



Regent nodded.



``Bitch?''



``Nobody left in my territory.''



``No threats?''



``Nobody.''



Coil sighed, ``I did tell you that you could run your territory as you wished.  Still, that's not ideal.  Would you object to a rearrangement of territory?  I would grant you more overall area to control, but it would be limited to the outskirts of the city.''



``So long as it's mine.''



``Good.  And Skitter?''



I shrugged.  ``No threats, nobody's daring to pop their heads in.''



``Then consider working on rooting out the individuals too afraid to show themselves, before they cause a problem.''



``They're dealt with,'' I said.



``Explain?''



``I'm doing two sweeps through my territory every day.  Only one yesterday, but we were busy dealing with the Chosen.  I'm checking every building for trouble.  If I find contraband, drugs or weapons, I confront the individuals in question.  Past two days, I haven't had to confront anyone.''



``The only people with weapons are your people, then?''



I nodded.  ``I've got sixty people working under me, and maybe a hundred more who are working for me in an indirect way, joining the community that's started on the cleanup projects.  Filling, moving and placing sandbags to control and reroute the flooding, clearing the area Burnscar burned down, and setting up accommodations.''



``Impressive,'' Coil said.



I nodded.  ``I feel like I'm cheating, though.  My power's suited to this.''



``It remains impressive.  Let me explain just why I find this of interest, Undersiders, Travelers.  The mayoral elections are in one week.  Before this occurs, I would like to have this city firmly in my control.  It will shift the tone and the aim of the election, which would be to my advantage.  \emph{Our} advantage.''



``So you're saying we have less than a week to wrap stuff up in our territory,'' Trickster said.



``Yes.  I also have some other issues I would like you to address.  Skitter, Genesis, I trust you're able to step away from your territories to give me a hand?''



Tattletale leaned forward over the table, looking at me.  I glanced at her, then turned to Coil, ``Yes.''



``Sure,'' Genesis said.



``And Trickster, if you're idle while you wait for your teammates to come assist with Purity's group, I'm sure you can lend your assistance for one night?''



Trickster nodded.



``The mayor and several members of the city council will be traveling to Washington to discuss the state of Brockton Bay and the possibility of condemning the city.  Skitter, Imp, Genesis, I would like you to visit him and ensure he argues towards \emph{our} ends.  Brockton Bay will stand, and it will recover.''



I nodded slowly.  ``Sure.  I think I can do that and still help Ballistic with Parian.''



``I haven't asked for your help,'' Ballistic said.



``Coil's call,'' I responded.



``If Skitter feels she can spare the time, I would be glad to have the extra assurance the job will get done.''



Ballistic folded his arms.  Didn't look happy at that.



``That's the last point of discussion.  I will provide anything you need to see your tasks to completion.  If there's no questions, that will be all.''



After a brief pause to check that nobody wanted to speak, we all stood from our seats.  The Travelers headed out the door and turned a right to go back to where Noelle was sealed up.  Tattletale led our group to the cells where Shatterbird and Victor were.



While we waited for Regent to go and bring Victfor out of his cell, Tattletale stepped close, so she was right next to Grue and me.  She murmured,  ``One piece of good news, two pieces of bad news and one spot of catastrophic news.  The good news is that Coil \emph{is} impressed with you, Skitter.''



``Okay,'' I said.  ``That's what we were hoping for, right?''



``But something tells me we've got a major snag.  I'd say odds are pretty fucking good that he's on to us.''



I felt my heart drop.



``How sure are you?'' I asked.



``Not positive, but \emph{pretty damn} sure.  And I'd say there's a fifty-fifty chance one of \emph{ours} informed him of our aims.''



``A member of the Undersiders?'' Grue asked.



``That, or he's got our places bugged.  But I didn't get the sense that anyone who built the place or brought our stuff in knew about any electronic bugging.  Like I said, fifty-fifty chance.''



I nodded.  I glanced around, looking at Bitch, Imp, and the door Regent had disappeared through.



``Fuck,'' Tattletale swore under her breath.  ``I was trying to signal you to say no to Coil's request, but you weren't looking at the right moments and I couldn't exactly tip anyone off.  I'm \emph{positive }he's asking you to go on that errand with Genesis and Trickster because he's planning on eliminating you.''



I felt Grue's hand squeeze my shoulder.  He'd gone rigid, as if he was more spooked than I was.



``And of course, he knows \emph{I} know.  So this is a loyalty test, I'm betting.  If you don't go, I flunk.''





