





We fell silent as Regent stepped out of the cell with Victor in tow.



``How's he handle?'' Tattletale asked.



``Like a Mercedes with an invisible, sticky gear shift,'' Regent said.



``Care to explain?''



Victor stretched, and said, ``Everything moves well, peak condition, but his power doesn't work so hot with him as a puppet.  Can't tell what I'm borrowing or who I'm stealing from.  I think I'd need his cooperation-''



Our captive sneered a little.



``-And I don't think he's willing to give it,'' Regent said.



``So the question is whether we want to take the time to try to convince him or take an indirect route,'' Grue said.



``Skitter's going to have to go in a few minutes, so let's see what you can do in the here and now?''



``Sure.''  Grue extended a hand and smothered Victor in darkness.  A second later, he said, ``I'm getting something.  Anyone here speak another language? \emph{Sug puppene til horemammaen din}?''



``No,'' Tattletale said.  ``You're getting that from Victor.''



``Can't really use it.  Now how do I change what I'm stealing?''



Tattletale shrugged.  ``It could be you're only picking up the surface stuff.  Here, Regent, try some martial arts forms.''



``Like what?  I don't know this stuff.''



``Victor does.  You fight using your puppets' muscle memory, right?  Try moving around, see what clicks and Grue will let you know if we're accomplishing anything.''



There was a pause.  Victor's hand briefly flashed out of the cloud of darkness as he shifted positions.



Grue rolled his shoulders some.  ``Yeah.  There's a martial art in there somewhere.  I'm picking something up, but it's slow.''



Tattletale smiled.  ``Take everything you can.  We'll see what sticks.''



``It's kind of depressing,'' Grue said, settling onto a stool, ``I always took some pride in honing my body, training, all that.  This feels like cheating.  Skipping the hard work.''



``You said you never had the time or interest to dedicate yourself to investing in a martial art,'' Tattletale pointed out.



``I didn't.  But that's not to say I wouldn't eventually.  A few years down the line, when things are quieter, I can see myself doing that, earning belts and learning to fight.''



``If you don't want to do this,'' Regent said, ``I could do something else with my day.''



Grue shook his head.  ``No.  It's fine.  Doesn't feel quite right, but I'll be able to do more to help you guys if I can fight better, if I'm more versatile.  And I'm getting another language, again.  Latin, I think.  Get him doing the forms again?''



Regent sighed.



Tattletale frowned, ``He's trying to drag you off course.  Using his brain to bring other stuff to the surface.  Listen, I'm going to see Skitter off, and then I'll talk to Coil, see if he has anyone who could drug Victor and mess with his mental functions without incapacitating him.''



\emph{Drugs, like the ones Coil's using on Dinah, }I thought.  And this would give Tattletale and me a chance to have some words about the hit Coil had put on my head.



I had to wonder\emph{ why? } I was arguably doing the best among his underlings.  Why was it so hard for him to simply let Dinah go, maybe take countermeasures to ensure she didn't betray him, and leave things alone?



I wouldn't be any threat to him if he wasn't doing something morally reprehensible.



We left Regent and Grue to their task and stepped out of the wing with the cells, venturing onto the metal walkway that overlooked the lower level.  I could see the Travelers at the vault door that kept Noelle contained, as well as the soldiers going about their business.



Which struck me as odd, when I thought about it.



``What's with the soldiers?'' I asked.  ``He's got, what, fifty or sixty here?''



``A little under that, but some are elsewhere.''



``Why?  I get that he was using them before, fighting Empire Eighty-Eight, but what's he using them for now?  He didn't send them against the Endbringer, he didn't use them against the Nine.  I get that he maybe fought off the Merchants and the Chosen when they were thriving, kept them from gaining too much steam, but it seems like a lot of money to spend on soldiers he doesn't intend to use.''



``Well,'' Tattletale said, leaning on the railing.  ``One, keeping them employed here means they won't be hired by someone else.''



``Right.''



``And I think they factor into his plan.  Either as a contingency or a greater aspect of it.''



I nodded.  I would have asked what that plan was, but I didn't want to say anything that would be too suspicious if overheard.  Not while we were on Coil's turf, especially.



Tattletale didn't seem to have those same concerns.  She leaned closer and murmured, ``You've got two jobs back to back.  That means you've got a few things to do.  Number one, if we've got a mole in our group and our communications are compromised, that means \emph{we} need a mole in Coil's group.  Someone that can inform us about any of Coil's movements he's wanting to keep concealed from us.''



``Ballistic?'' I asked.



``Mm,'' she murmured a response.  ``Sound him out.  Be careful about it, but try to get a sense of how tight he is with the rest of the Travelers.  Like Cherish said, Trickster isn't tight with his team.  See just how un-tight Ballistic is with his boss, and maybe we can make some inroads.''



``Okay.''



``That won't be easy, because I get the sense he doesn't like you, and he's upset you've stepped on his toes here.''



I frowned.



``The second thing?  About the possible murder attempt?''  She asked.



``Just a little worried about that.''



``He only decided it as recently as this morning, so anything he's set up is going to happen later.''



``And you don't know how he's going to approach this, or what he'll do?''



She shook her head.  ``All I know is that Coil's intending for it to happen tonight, probably related to your job with the mayor.''



``And you're positive on this?''



``It's one of those things where everything clicks into place perfectly if we acknowledge this one fact: he wants to kill you.  For example, he has more reasons to send Imp than to send Trickster.''



``How's that work?''



``I've already filled Imp in on this, but Coil's concerned about Grue's emotional state and what it means for our team as a whole.''



I nodded.  \emph{Which means he wants to remove Imp from the picture to see how Grue handles himself}.



``So we're keeping that on the down-low.  I'm not sure when we'll be able to do it, but I've talked with Imp and Regent, and sort of hinted on the subject with Bitch, and we might be looking at making you our team leader.  At least for a little while.''



I snapped my head around to look at her.



``It makes the most sense.  You have the best grip on who's in play and how to use our abilities.  You think tactically,'' she murmured.



``Why not you?''  I asked.  ``You have seniority, you have more experience, you can apparently keep track of Imp, and you can identify our enemy's weaknesses.''



``I'm not sure I have more experience,'' Tattletale admitted, ``Or at least, my experience doesn't count for much.  Robbing software companies and casinos doesn't really compare to going toe to toe with Mannequin.''



``My other points stand.''



``Just because we're putting you in charge doesn't mean I can't still handle that stuff.  If you want to delegate to me at any point, that's fine.  It's just a question of who we turn to when we need a spur of the moment decision.''



``I'm not good at those.  I'm only good when I can plan, consider everything that's at play.''



``I don't think you give yourself credit.  I've said it before, I'll say it again, you're good at improvising.''



``With just me, \emph{maybe}.  Just my own abilities.  I'm not sure I can do that if I'm also worrying about the four of you.''



``We'll have to see in the field.  Unless you're really going to argue Grue's going to be able to hold his own in a high pressure situation?''



I frowned behind my mask and shook my head.



``Of course, discussing this means nothing if you get killed.  Don't.''



``Easy as that?  Don't get killed?''



``You're going into a tricky situation with the most amoral member and the most versatile member of their group.  Keep an eye on everything and try to be unpredictable so they can't get you in a trap.''



I just had to figure out how to do that with a job this cut and dry.



``Ballistic's coming,'' Tattletale said.  I looked and saw Ballistic ascending the staircase at the far end of the walkway.  It would take him a minute or three to join us.



``Any final tips before I'm left with him?''



``He's angry.  Coil's roped in the Travelers by promising to help them with Noelle, but there's two snags in that which we may be able to use.  For one thing, I don't know if Coil seriously intends to offer any fix he does find.  For another, Ballistic cares less about that than anyone else.  Or maybe it would be better to say he almost doesn't want to help with that because Trickster wants it so badly.''



``That sounds like it's less about team friction and more about sheer enmity.''



``I think they were really good friends once and now they're distant.''



Well, it wasn't like I wasn't unfamiliar with that idea.



``And,'' she said, her voice low, ``I \emph{can} tell you the Noelle thing isn't the only crisis they're working on handling.  The focus on Noelle is something of a sore point with Ballistic.''



``Vague.  And I can't really say anything about that without admitting the info came from you.''



``Yeah,'' she said.  Then she straightened, turning toward Ballistic.



``That huddle looked like a conspiracy at work,'' he commented.  He looked like he'd based his costume off of the capes of a different era, with only some concessions made to fitting in with his team's color scheme; a costume in black with red patterns on the fabric, heavy on the armor panels and padding, making a big guy look even bigger.  His mask was square, with holes only for the eyes.  Belts and pouches were strapped across his entire body.



``Conspiracy?  Us?''  Tattletale grinned.



``You were whispering about something.''



``Boys,'' she said, winking.



``Hm,'' he didn't look impressed.



``No, we really were talking about boys.  About Grue, specifically, and maybe replacing him as leader.''



``Hey,'' I said, before I'd processed \emph{why} she was saying that.  She wanted to earn some measure of trust by volunteering a secret.



She shrugged.  ``They're going to find out eventually.  We'll have to trust Ballistic to not go running to Coil to tell on us.''



He folded his arms.  ``Putting me in a compromising spot?''



``Sure.  You can handle it,'' she told him.  She gave me a pat on the shoulder, ``I'm going to see about those drugs for Victor.  Good luck to you two.''



``Tell me,'' Ballistic said, as Tattletale strolled off, ``Do you ever get past that point where you feel painfully uncomfortable around her?''



``Yeah,'' I said.  ``You get over that with time.''



I didn't add that the discomfort he was describing was largely linked to the number of secrets one was trying to keep from her.  It almost went without saying.



``You're still insisting on coming along?'' he asked.  ``You know I can handle this on my own.''



``I don't doubt that.  But I'm kind of wanting to see this place.''



``\emph{Why}?''



``I'm running my own territory.  Maybe there are ideas I can use.  And I want to see how people are coping in other districts.''



``I'd ask `why' again, but I'm not sure I'd get it.''



``If this city doesn't get condemned, you're going to have people moving into your district.  Even after the city's infrastructure is up and running again, those people are going to put pressure on you for certain things.''



``See, you're approaching this like a medieval lord, managing her serfs and servants and I see this more as being a watchdog.''



I gestured toward the exit, and he sighed.  We began making our way out of the base.



``Do you really want to limit yourself to being a watchdog?''



``When I'm making this much cash?  When even the top guys in this town would run scared from me?  Sure.''  He held the door open for me.



``And that's all it comes down to?  Cash and being feared?''



``I'm a living gun and my surroundings are nothing but piles of ammunition.  What do you expect?  You don't think \emph{you're} scary?''



``I think you can have money and power, you can be fearsome where necessary, but you can still make a difference at the same time.''



``Doesn't seem worth it, working your ass off to make some people a little happier and more comfortable before the world ends.''



``You're one of the people that's fixated on that, huh?''



``The world's gonna end.  How can you shrug that off?''



``It might not.''



``Right,'' he said, clearly humoring me.



This wasn't working.  Tattletale had said Ballistic was angry, but I'd taken that to be the same sort of anger that Bitch harbored.  Whatever was going on with Noelle and the group dynamics that had Sundancer so unhappy, it had made Ballistic angry at the world, angry at circumstance.  A different sort of anger, really: he didn't really care about anything or anyone.



How was I supposed to get through to him if that was the case?



I decided to call him on it.



``Okay, so your only priorities are money and power?  Then why are you so annoyed that I'm coming along?  What does it matter?''



``It's my business, my territory, and I'm capable of handling her on my own.  It's insulting that \emph{Coil} thinks I'd need any help, and it's \emph{rude} that you'd volunteer yourself without checking with me first.''



``Okay,'' I said.  ``Hypothetically, just going by what you were saying earlier, why should I give a damn?  The world's going to end in a few years anyways.  What does it matter if I get on your bad side?''



``That's different,'' he said, sounding annoyed.



``Why?  Because it's \emph{you} that's getting shortchanged?''



``Because we're basically coworkers.  If we're going to have to fight alongside one another, we can't be worried about this sort of thing.''



``Okay, first of all?  I have a closer working relationship with the people in my territory than I do with any of the Travelers.  If and when you get more people in your territory, you might find that's the same with you, too.  So I'm not sure I buy that coworker thing.''



``You're talking apples and oranges.  Capes and non-capes.''



``Fine.''  He'd left an opening for me to target.  ``Then I'll just point to your other `coworkers'.  The other Travelers.  There's obvious friction.  There's resentment.  Cherish said as much.  So I don't think \emph{you} buy the coworker thing either.''



``Again, that's different.''



``You say that a lot.  Maybe this principle you're living by isn't that strong if it can't hold up to the most basic arguments.  Unless you care to explain \emph{why} that's different?''



``You're grilling me for info on my team.''



``I'm curious what's going on there, yeah.  But I'm also trying to figure you out.  As you said, we're coworkers.''



``Weren't you just debating the coworker thing?''



``Decide if you really believe it, let me know, and I'll change my argument accordingly,'' I said.



He sighed.



``I'm not trying to get on your bad side,'' I said.  ``Really.  But I've dealt with some interesting personalities like Bitch, Regent and Imp for a little while now, and I know I won't be able to communicate with you until I understand where you're coming from.  So I'm willing to go the extra mile to figure you out \emph{now} so I can understand you in the future\ldots''



I trailed off, but I kept one eye on him to see if there was any hint that he knew about Coil's plans to terminate my future.  There was nothing.  I couldn't see his face, but nothing had changed in his posture, his stride or overall body language.



``You're not going to stop digging and get off my case here, huh?''  He asked.



I was mentally categorizing him as very similar to Bitch in many respects.  He was smarter, though, and the weapons he wielded in a discussion were less about threatening imminent harm than, what?  Setting himself further apart from me?  Breaking ties, categorizing me as an enemy in his head and making dealing with him harder in the future?



It would explain why there was a schism between him and the other members of his group.



``If you ask me to?  I'll back off.  But\ldots'' I made the call on the spur of the moment, as I might with Bitch if I were positive she wasn't about to hit me.  ``I think you and I would both agree that you'd be admitting I'm right if you did.''



``That's dirty.''



``Sure.''



``So what do you want to know, then?  Shall I divulge my deepest, darkest secrets?''



``I'll settle for knowing why you're all so angry at Trickster, why \emph{you} specifically are angry at him.''



``Nope.  Can't say.''



``Can't or won't?''



``Won't.  We made a deal, and that deal means we've kept some stuff from Coil, even.  I'm not about to tell you.''



``I don't need to know specifics.''



``You don't need to know the general details, either.''



``Not really.  But maybe \emph{you} need to tell me?  One of your teammates said they were awfully lonely, and they're closer with the rest of the team than you are.  Maybe you're lonely too, nobody to vent to?''



``I'm a guy.  We don't do the whole emotional sharing thing.  You trying to channel Tattletale here?  Why are you so intent on getting the details, here?  This isn't just curiosity or wanting to know your coworkers.''



\emph{Because so much hinges on my ability to get you on board against Coil}.



I didn't have a good response, so I fell silent.  We continued walking down the streets towards the crater-lake, our footsteps sloshing in the shallow water.



``He took everything from us,'' Ballistic said, breaking the silence.



``Trickster?''



``Trickster.  When everything started falling apart, he stepped up to make the calls.  Bad ones.  And now the group is all we have left.  No friends, no family, no home to go back to, no goals beyond fixing Trickster's fuckups.''



I was thinking of how it had come out that Sundancer was reluctant to use her powers because of the damage she'd done in the past.  Civilian deaths?  Had they included their own families?  Had Noelle been included in that?



It might explain why they were so gun-shy about using their powers to their fullest potential and why they'd been so insistent on keeping Noelle locked up when we were up against the Nine.



He went on, ``The others might hate Trickster but they still respect him.  Or they don't respect him but they don't hate him either.  Probably more the former than the latter.  But I don't have any love for the guy, I don't have any respect for him either, and I seem to be alone in that.''



``So where do you go from there?''



``Now we're back to square one.  I already explained.  Money, being feared, respect and living in comfort as a badass watchdog.''



``All that stuff about hating him, blaming him for ruining your life, and you don't want any revenge on him?'' I asked, as casually as I could manage.



``No.  I'm with the group for one reason.  I stick with shit.  Not going to turn on the guy.  I agreed to this thing with Coil because I thought it'd be a way to get back some of what we've lost, maybe.  But all I see is my teammates getting all starry-eyed with hope while Coil feeds us empty promises.  Saying Tattletale will find an answer, or he'll make a request to some major scientists in parahuman study.  And of course there's no answers.''



``There could be.''



``Nah.  Why would he give us what we want if it means losing our services?  But I don't really care anymore.  I made a deal with Coil and I'll stick that through until I have a good reason not to.  Way I figure it, fuck my team, fuck Coil, but it's not worth confronting anyone over if it means I'm wasting the remaining two years of my life trying to get another gig this cushy.''



``That seems kind of claustrophobic, setting those restrictions on yourself, letting things with your team drop by the wayside.  Being all alone?''



``Won't be alone.  Figure I've got enough cash and respect I can get groupies.  That'll do for the next couple of years.  Unless you're going to argue there's some point to a committed, long term relationship when there's no long term?''



I sighed.  There was no point in continuing this.  I could tell that Ballistic wasn't going to budge, and I didn't have a `good reason' to convince him to join us.



We crossed several city blocks in silence.  When we'd reached the lake Leviathan had created downtown, we began to walk around to the north end to Dolltown.



``So how are we doing this?  Attack strategy?''  Ballistic asked.



``Any chance you'll let me make the first move?''



``And take all the credit?''  His voice hardened.



``I'll let you take half the credit if I'm successful.  You can take \emph{all} the credit if I fail.''



``Nope.''



``What?''



``I get what you're doing.  You want to make us Travelers look bad.  Get yourself a bigger slice of the pie somewhere down the road.  More respect, more power, and you're doing that by wedging yourself into everything, getting hyperinvolved.  Gotta be in first place.''



``That's crazy.''



``Right.  Then explain why you're going overboard with your territory.''



``I'm getting the job done, taking care of my people.''



``Nah.  It's more than that.  There's something driving you to work that hard.  You're looking to supplant us.''



He'd stopped walking.  I paused and turned to face him.



He chuckled lightly, ``I don't \emph{blame} you for it.  I mean, it's pretty scummy, when we're supposed to be working together, but I get that you want to be on top.''



``We \emph{are }working together.''



``I may be taller and in better shape than average, but I'm not \emph{dumb}.  You think I didn't catch the wedge you were trying to drive into our team?  Sounding me out for any hard feelings I might have for the others?''



\emph{Shit.  }This sort of thing was Tattletale's field, not mine.  Now it was going south fast, and I could imagine how this would explode in my face.



I cleared my throat a little and clarified, ``I was sounding you out because it was clear you \emph{did} have hard feelings for the other members of your team, and I wanted to give you a chance to talk about it.''



``Ah, so the creepy bug girl is really a softie in the end,'' his voice was laced with sarcasm.  ``No ulterior motives at all.''



``Whatever,'' I said.  ``Nevermind.''



``So fuck you,'' he said.  ``No, I'm not giving you first dibs on this doll woman.  Second I see her, I'm taking her out of action and making it a hundred percent clear it was all my doing.  You'll get what you wanted, which you said was to see the territory, and I get what I want, which is to finish up my territory so I can kick back.''



This wasn't how I wanted things to go on any level.  I could have groaned in frustration.  Instead, I sent out a command to my bugs and took a deep breath.



``Okay,'' I told him.



``Yeah?''



``But I think I'll stay out of the line of fire.  I get the impression I offended you, so maybe we give each other some breathing room?  Avoid getting shot?''



``I wouldn't jeopardize the setup I've got with Coil for that.  But maybe it's best you do stay out of the way.''



I nodded and turned to go.



Okay, so no mole inside the Travelers.



I could still hope to achieve \emph{something} here.



Using my bugs, I tracked Parian's movements within Dolltown.  She was moving quickly, joined by a small collection of people.  Many were shrouded in cloth, leaving me to guess if they were real people or something new she'd done with her creations.



I drew out directions with my bugs, guiding her away from Ballistic.  She didn't listen at first, but that changed when Ballistic fired off his first attack, creating a deafening crash.  From the sound of it, he'd done something to send a car flying into a building.  A moment later, he did it again.  I walked faster.  I could call Atlas to me, but I didn't want to get spotted in the air.



Dolltown was ugly.  It had been hit hard by the Nine and the fight between them and Hookwolf's army.  There were scars on the buildings where Hookwolf had struck, holes and marks in the wall where Purity had fired her beams.  Menja had done some damage here and there, with some handprints marking various pieces of architecture where her gauntlets had bit into stone and metal.



I pushed open a doorway and stepped into a ruined building.  Parian faced me.  Her mask had a crack in it, and there was blood staining her worn frock.  She was surrounded by a half-dozen of her remaining people, each of whom wore masks and costumes.  A life-size doll, a man who was wrapped in fabric to the point that he looked something like a mummy, a little girl in a skintight suit of flannel with holes cut out for the eyes, one blue and one green.



Did Parian have capes working for her?  Or-



No.



They were the people Bonesaw had done surgery on.  The ones she'd altered to look like members of the Nine.  They were covering the faces and bodies Bonesaw had given them.



``What do you want?''  Parian asked.



``To negotiate,'' I said.



``Your buddy isn't too interested in negotiating, by the sounds of it,'' she said.  She flinched as another crash sounded somewhere nearby.



``I took a gamble here, warning you about him.  He wanted to hurt you, make you into an example.  I don't operate that way.''



``Don't think I can trust you on that.''



``You'll have to.  Because I've gone around Ballistic's back, I'm kind of counting on you hearing me out, because if I fail here, it's going to fuck up things with this alliance my team has with the Travelers.''  \emph{And with Coil}.



She glanced around.  I could sense someone moving nearby.  One of her people, sneaking up behind me.  No gun, a light search with my bugs told me, and more of the same cloth costume the other Dolltown residents were wearing.  I ignored my potential assailant.  I could handle an attack from a knife.  I'd just need to be on guard in case they aimed to club me over the head.



``I know about the person that's circling around to ambush me,'' I said.  ``Can we just talk, without someone trying to hurt me?''



``What are you wanting to \emph{talk} about, then?''



``You got dealt a raw hand.  The Nine targeted you, like they targeted some people I care about.  People I love.  That's not fair.  So I was thinking, I've got a lot of money.  I have access to resources.  I know it's not much, it's not really enough, but maybe we could get doctors for your friends and family.  Fix what's been done to them.''



``And what would you want in exchange?''



``Join my team,'' I said.  ``I-''



``No.''



``\emph{Listen},'' I hissed the word, ``It's the best way to guarantee safety for everyone here.  It gets Ballistic off your back.  Even if you avoid him today, he's going to level half of Dolltown, and he'll come back tomorrow to level the other half.  Everything else would stay the same, you'd have the same freedoms, only we'd supply you with everything you need.  Not just rice and fresh water, but \emph{good}\emph{food.  }Medical care.  Proper shelter.  All you need to offer is lip service and we can fix so many of the things that have gone wrong here.''



The person behind me stepped closer.  I turned to keep an eye on her and she lunged in that same instant.



Three spikes of metal were sticking out from between her fingers, like improvised brass knuckles.  When she punched them into my shoulder, they went straight through my costume, piercing through the bone as though they were hot knives and I were nothing but soft butter.  She swept my feet from under me and pushed me to the ground.



``The lady said no,'' Flechette told me, one hand holding me down, the other hand raised to strike me again.





