





Not my brightest move, I had to admit.  The problem with acting like I was tough enough to shrug off an attack from a knife wielder was that the illusion failed pretty damn hard when I actually got stabbed.



I'd been relying too much on my costume.



``If I see a single bug, I'll be forced to use this,'' Flechette said, angling the spike of metal in her hand so I could see it better.



``Isn't that going too far?'' Parian asked, her voice small.



``No,'' Flechette said.  Her hand was still poised to strike the second I moved.



``She was just talking.''



``She \emph{just talked} to Panacea, if you remember.  And I told you before, the last time Glory Girl was seen was in her company.  I've explained what happened after that.''



``You think \emph{she} did it?''



\emph{Did what?}



``I think the thinker-seven on her team might have.  Running theory is that Tattletale has a clairvoyance that lets her see weak points.  Finds the points to attack in people, security systems, patrol routes, reverse-engineers the results to get general information.''



\emph{Okay, }she'd hit the key points, but sort of got it backwards.



``That was Jack,'' I said.  ``Jack was the one who got to Amy.''



``Occam's razor.  Most likely answer is often the correct one.  Or something like that,'' Flechette said,  ``Is it going to be Jack, who has powers we already know?  Or is it going to be Tattletale, who has set down more than enough precedent for that kind of behavior and a still-unknown power?  It fits what your group's trying to do, taking over the city for yourselves.  \emph{And} I should point out that records \emph{do }seem to point to people being left devastated or ruined wherever you go.  Panacea, Armsmaster, the Slaughterhouse Nine--''



``You're \emph{complaining} about us taking out the Nine?  And that wasn't all us.  It wasn't even \emph{mostly} us.  That was everything going to hell and people with issues getting pushed past their limits.  We were only involved because we've tried to help every step of the way.''



``You think she was going to do to me what she did to Glory Girl and Panacea?'' Parian asked.



``I'd say the possibility exists,'' Flechette said. ``And that's reason enough to be \emph{very} careful.''



\emph{Damn this}.  ``I'm not trying to fucking corrupt or psychologically traumatize Parian.  Or anyone else!  \emph{Yes, }we're trying to take over the city.  \emph{Yes}, we're currently working on eliminating the competition--''



``Mm,'' Flechette murmured, her expression hard.



``But that's not why I'm here, not exactly.  It serves our goals just as well if I recruit Parian.  It's one person out of the way, and it gives us a way to help people who need it.''



``So you say.''



``\emph{Fuck}, I hate it when people do that.  `Everything you say is a lie, including any protests or arguments over the fact that you're a liar.'''



There was a crash, further away than the last.  Ballistic had headed in a different direction.  For the moment, at least, we were out of harm's way.



``You're sort of well-known in the community for being deceptive and underhanded.''



``Because of what Armsmaster said at the hospital?''



``In part.''



``Is nobody paying attention to the fact that he was seriously bent in the head?  To the point that the \emph{Slaughterhouse}\emph{Nine} thought he was a good candidate for their group?''



``Mannequin targeted Armsmaster to mess with him.  It's his M.O..  He goes out of his way to attack and ruin tinkers and other individuals who could do something for society.''



``I love how the so-called `good' guys get to revise events to make stuff more convenient for them.''



``It's a perk.  People tend to trust your version of events when you're doing what's right,'' Flechette said.  The spike she gripped between two fingers tapped against my throat, but didn't pierce the fabric.  She wasn't using her power or she could have killed me.



``You're implying that you guys are doing what's `right' that much more often than we are.''



``That should be obvious.''



``And you really believe that?''



``Have to.''



``Do you know \emph{why }Armsmaster was arrested?''



``He wasn't.''



``Unofficially arrested, then.  Do you know why he was cooped up in the local PRT headquarters, with no official title or role?''



``He was in therapy for his injury.  He lost an arm.''



``I know.  I was there when Leviathan tore it out of the socket.  I applied pressure to the wound to try to stop the blood loss.  But that's not why they locked him up.  They could have given him an administrative position if it was just an injury, and they didn't.''



``Maybe they did.  It's not like either of us were there when the decisions were made.''



``With no job title?  They didn't list one for him, and with the state of the city, they could have leveraged his reputation alone to boost morale, just by saying Armsmaster was in charge of the local task-forces.''



``There's emotional stress with permanent injuries, too.''



``Plenty of people under just as much stress, if not more, after the Endbringer hit.  But I'll admit your perspective's better than mine,'' I said, looking up at her.  ``You joined the Wards just in time to see the aftermath of Gallant and Aegis dying.  How did they handle that?  If the PRT was that accommodating with Armsmaster, I'm sure they arranged for therapy and time off for all the Wards.''



``Yes to therapy,'' she said.  ``No to the time off.  Too much to take care of.''



``Oh?'' I asked.  I hadn't honestly expected them to enforce and allow for therapy.  It threw me off my stride.



``Why are you so surprised?  And where is this coming from?  Tattletale feed you this information?''



``Only some of the general details, like what Armsmaster was up to.  The bit about the PRT dropping the ball in taking care of you guys was mainly drawn from past experience.''



``But they didn't.''



``Flechette,'' Parian spoke up, ``Weren't you saying it was \emph{Weld} who pushed for the therapy?''



Flechette shot her a look, as if she were thinking, \emph{Whose side are you on}?



``Wards taking care of Wards,'' I said.  ``Okay, I think my argument stands.  No reason to suggest that Armsmaster was being coddled to that degree for any emotional or mental distress he went through.''



``What are you getting at?''



``I'm saying he was \emph{arrested}.  Off the books.  And there aren't really any reasonable explanations to the contrary.  People are still taking his word on events, taking his word on \emph{me}, but he was as fucked up as any of us.''



``Given the choice, I'm going to take his word over yours, sorry.''



``That's what I'm saying is \emph{screwed up}!''  I hissed the last two words.  ``Why?  Because of the label he chose to identify by?  He calls himself a hero and he gets more credit?''



``Because he put in a good fifteen years of hard work to improve this city, and because I think your perspective's warped.''



``\emph{Everyone} has a screwed up perspective!  Especially here, especially now, with the way this city is.  My perspective's fucked up because everyone I was supposed to rely on dropped the ball, and the only people I could count on were crooks!  Panacea got warped because her parents let her down, because nobody ever sat down and talked to her about who her dad was.  So she convinced herself that she was doomed to follow in his footsteps.''



``How do you know that?''



``I was \emph{there}!  I, we, tried to help.  But she's never had someone \emph{talk} to her, so she didn't know how to listen to us.  Which is probably a blessing in disguise, because she didn't listen to Jack or Bonesaw either.''



Flechette gave me a funny look.  Her eyes were vague shadows behind her visor, but I could see one distort in size as she raised an eyebrow.



``What?''  I asked.  Something about Panacea and Glory Girl?  She'd said something earlier too.



She spoke, interrupting my thoughts before I could frame them into a question.  ``Nothing.  I guess you're going to tell me you tried to help Armsmaster too?''



``No.  I turned to him for help, and he tried to screw me over.  I joined the Undersiders to give him the details he wanted on their powers and methods and he not only hung me out to dry, but he tried to \emph{kill} me.  He \emph{did} kill Kaiser and Fenja, nearly killed Kid Win by accident, and there were others there too.  All for his own personal glory.  Because he had some kind of crazy tunnel-vision when it came to his personal ambition and successes.''



Flechette frowned.



I took the chance to hammer my point home.  ``He knew I was just an undercover agent, but he thought my death and the casual sacrifices of the others who had chosen to risk their lives to stop Leviathan were worth getting a \emph{personal} shot at killing Leviathan one on one.''



``What?'' Parian asked.  ``\emph{Seriously}?  Doesn't that violate the deal with--''



``Yes,'' Flechette cut her off.  ``Yes it would.''



I shrugged, looking at Flechette, Parian and the Dolltown residents.  ``Probably going to get in trouble for revealing that, but I'll leave it to you to decide what to do with that information.  I'm already a priority target anyways, pretty much, what with our intended takeover of the city.''



``You seem to be missing the point that you're under arrest \emph{right now},'' Flechette spoke.



I sighed.  ``And nothing I say is getting through.''



``It's exactly what I was talking about before, you're just using information Tattletale fed you to try to screw with my head, fill me with doubts and paranoia.''



``And how would I know you'd be here?  I'd have to get the information from her in advance, remember?''



``Tattletale told you I'd be here.''



\emph{Okay, that's admittedly possible}.



``So your interpretation of events is that I knew you were here, I came prepared with all this made up information on Armsmaster to mess with you, and I just let you stab me?''



As if mentioning it reminded my brain, I could feel the pain radiating from my shoulder.  At least she'd left the spike in there.  It seemed even better at preventing the bleeding than I'd guessed it would be.  A snug fit?  I wouldn't bleed to death in the next ten minutes.



She didn't venture a response.



``Flechette, if you don't believe me, you can look at the armband Dragon gave us for the fight against Leviathan.  Armsmaster fried it with an EMP to keep me from broadcasting Leviathan's location to anyone, and then he moved in only after he'd thought Leviathan had killed me.  It's on top of a ceiling panel in the shelter on Slater street.  Women's bathroom, above the middle toilet.  I couldn't keep it in case Dragon used it to track me down, but you can go grab it if she hasn't sent someone already.  Get a tinker you trust to look at it.''



``The results could be fabricated.''



``Tell your tinker that.  He'll keep it in mind, and he can tell you the likelihood of it being something I'm doing to frame Armsmaster versus it being Armsmaster's work.''



``Why are you telling me this?''



``Because I'm trying to convince you that `right' isn't the exclusive property of the good guys, just like `wrong' isn't wholly on our side of the fence.  Armsmaster's sense of `good' was purely what was \emph{good} for his own interests.  I'm trying to do the right thing more often than not, believe it or not, or I'm doing the wrong things for the right reasons.''



``And which were you doing here, trying to recruit Parian?''



I glanced at Parian, ``I don't know yet.  Thinking it's more the latter.''



There was a rumble as Ballistic knocked over a building somewhere a distance away.



``We don't need your help,'' Flechette said.



``Don't you?  I don't know why you're wearing that getup, but I'm assuming those other people are because of what Bonesaw did.''



I could see the people in the concealing costumes shifting uncomfortably.



``Why I'm in this costume isn't any of your business.  I'm here to help.''



``I can help \emph{more}.  I can get them medical attention, start reversing what the Slaughterhouse Nine did to them.''



Parian spoke, her voice quiet, ``So you're asking me to choose between being loyal to a friend who's helped me, comforted me and kept me sane these past few weeks, or selling my soul for the\ldots supposed greater good.''



``Saying you'd be selling your soul is a bit overdramatic,'' I said.



``I'm an artist, I'm dramatic by nature.''



``Then let me make an emotional appeal.  Come to my territory.  Let me show you what I'm doing there, and what I want to help you do for your people.''



``You'll just take the advantage of the situation to escape,'' Flechette said.



``I don't really think you can keep me,'' I said, sounding calmer than I felt.



``We'll see,'' she responded.



I sent a command to Atlas.



``Easiest option is that I send a message to Ballistic.  I really don't want to do that, because it's going to get people hurt or killed.''



``His files say he doesn't kill,'' she responded.



``With his power?  It's easy to accidentally go too far.  Combine that with the sheer danger your own power presents?  It's like playing tag with guns.  Not saying I don't respect your power, with the damage you did to Leviathan, but he can escalate harder and faster than you.  If you two get in a shootout, someone's going to get hurt.''



As if to punctuate my statement, there was a sound of a building collapsing nearby.



``Well then,'' Flechette said.  She adjusted her grip on the spike of metal that she held between her fingers.  A dart.  She poked it through the armor of my wrist.  When I tried to move my arm, it was fixed to the ground.  ``I guess I'll come back for you later, after Ballistic's left.''



``Undo it, release me,'' I said, pulling harder.



``No.  And stop struggling.  Unless you can tear that costume, you're not going to pull free.  It's bonded.''



``You're making a mistake,'' I growled.  ``I'm only trying to help.''



``And I'm doing my job.  I get that maybe your intentions are good, but I'm obligated to take you in, especially now that I've heard your confession of intent to seize the city.''



``How many wrongs have been done by people who were `just following orders'?'' I asked.



I directed Atlas in through an open window.  Every set of eyes was on Flechette and I, which made it easy for him to slip into the room.  My bugs had identified tripwires Parian had set, and navigating Atlas around them wasn't too hard.



``Stop it!''  Parian cried.  For a second, I thought it had to do with Atlas, but her shout followed within a second of my question to Flechette.



Flechette looked like she'd been slapped.  I stopped Atlas where he was, poised a few feet behind Parian.  I folded his scythe-like claws down and out of the way.



``Skitter\ldots if we let you go, do you promise not to attack or interfere under any circumstance?''



``Parian?''  Flechette asked.  She sounded almost hurt.



``It depends, are you going to go confront Ballistic?''



``Honestly?  Yes.  You said he'd keep coming until he took us out.''



I frowned, but they couldn't see that behind my mask.  Ballistic was angry, he was dangerous, and there was little to nothing tying him to Coil's service, outside of some vague sense of duty.



``Are you going to arrest him?'' I asked.



``No,'' Parian responded, at the same time Flechette said, ``Yes.''



``We could scare him off,'' Parian said.  ``Beat him up a little.''



``And he'd bring in the other Travelers and Undersiders to wipe us out,'' Flechette said.



Parian looked at me, ``He wouldn't, would he?''



I nodded, ``He would.''



Parian sagged, dropping into a sitting position.  Flechette turned to look at her and froze.  ``What the hell is that?''



She'd seen Atlas.



``I brought him in here as insurance,'' I said.  ``I was thinking about taking Parian hostage if you went ahead with my arrest, but she started being reasonable and I told him to back down.''



``What \emph{is} he?''



``Panacea made him for me, for fighting the Nine.  Just a big beetle with sharp claws.''



``\emph{That's} what you were using to fly around, when we were fighting the Nine?''



I nodded.



``Creepy.''



``Look,'' I said, seeing a chance to regain control of the conversation.  ``I'll extend my offer a third time.  Join us, Parian.  We're not as scary or as bad as we look at first glance.  You'll see that if you check out my territory.  I'm not threatening you or extorting this out of you.  You can say no--''



``Because I have a weapon at your throat,'' Flechette said.



``Because it's \emph{her call},'' I said, my voice firm.  ``Because I really do think she'll be safer overall.''



``From those people who `aren't as scary or bad at first glance','' Flechette said.



``From all the other capes and unpowered individuals who would prey on her and her people.''



``I can't,'' Parian said.  ``No.  I have to turn down your offer.''



I sighed.  \emph{Damn.  Damn, damn, damn.  }``Can I ask why?''



``Flechette's done too much to help me, to help \emph{us}, for me to turn around and become her enemy.  Even if it's for the greater good.  And maybe they won't forgive me for it, but I can't agree to short-term gains, to giving them some medical care and reconstructive surgery now, in exchange for becoming a criminal for the rest of my life.''



``What if this was temporary?''  \emph{Can't reveal too much.  Can't let them know Coil's reign ends soon, if everything goes according to plan}.



``I'd still carry the label, wouldn't I?  Maybe I don't agree with \emph{everything} Flechette said, but I do agree that just calling myself a villain, even for a short time, it wouldn't be something I could shake so easily.  We'll find another way.  I can use my power to make money, I'll heal them.  I'll make up for failing to protect them.''



A woman with a cloth hood covering everything but one eye reached out and put a hand on Parian's shoulder, squeezed.



She felt the same kind of responsibility for her people that I did for mine.  The realization made me all the more disappointed that she'd said no.



``Okay,'' I said.  ``Flechette, I'm going to reach behind my back.  I'm not drawing a weapon.''



``No,'' she said, ``Whatever deals Parian is making, they don't change the fact that you're under arrest.  I have to do my job, and with the Nine gone, your faction is a priority.  \emph{Especially} with your suspected involvement in the incident with Glory Girl and Panacea.''



I frowned.  I needed another option.  My armor was loaded down with bugs, and that included the compartment.  I could \emph{feel} what I needed.  It was just a question of getting it free.



Spiders drew silk around the object in question, then made their way across my shoulder and up the back of my arm, braiding the threads together as they went and hooking them against the edges of my armor to get traction in the right areas.  They reached my hand and encircled one finger.



I twitched that finger and tugged the thread.  Another, harder pull, and it came free.   My bugs muffled the sound of the object hitting ground.



``What was that?'' Flechette asked.



As a mass, they carried the object into plain view.  My cell phone.



``You make the call, so you know I'm not trying something,'' I said.



Flechette frowned.  ``There's no reason.''



``There's a \emph{great} reason, but I don't think you'll believe me if we don't do things my way.  Password to unlock the phone is seven-two-eight-one.''



She picked up the phone and threw it over her shoulder at Parian.  Parian caught it.



``Me?''



``I'm keeping my attention on Skitter.  Don't forget to watch that beetle of hers while you're making the call.''



Parian nodded, too quickly.  ``What was that number?''



``Seven-two-eight-one.''



``Okay.''



``Go to the contact list.''



``It's all gibberish.  Symbols and numbers and stuff.''



``It's a code.  First number that starts with heart-star-colon.''



``Okay.  It's ringing.  Should I put it on speaker phone?''



``No,'' Flechette said.



``Tell her you're speaking on behalf of Skitter,'' I said.



Parian nodded.  ``Um.  Hi?  I'm speaking for Skitter.''



``Tell her--''



``She just said, um, Emerald-S.''



``Tell her Celery-A.''



``Celery-A.  Okay.''



``Upstairs, beneath the workbench, to the bottom-left of the painting, there's a panel.  Tell her to remove it.''



Parian relayed the instructions.  There was a pause of no less than two minutes before she said,  ``The girl on the other end says there's a safe.''



``Six-one-one,'' I paused to let Parian relay the numbers, ``Two-zero-three\ldots one-zero-zero\ldots six-six-three.''



``It's open.  She says there's stacks of money?''



``Tell her to gather two hundred thousand dollars from the safe, pick five people who need a break from work, C included.  Only C should know about it, I don't want the others to get greedy.  They can pack it into a truck, head north and meet you just before the ramp where Lord Street turns on to the ninety-five.''



``I don't understand.''



``Leave this city, Parian.  There's nothing good left here anymore.  That money's yours.  Use it to heal and help the friends and family you still have left.  Get out of here, use the money to get yourselves settled, get some therapy for everything you've been through, and go pursue that career in fashion you said you wanted.''



``\emph{Why}?''



``There's been too much ugliness here.  There's bound to be more.  I\ldots I guess I have the money, and you need it.  And I guess I feel complicit in what happened.  The Nine did what they did to Dolltown because we'd forced them into a corner.  Maybe they would have attacked anyways, they were headed your way.  I don't know, but let me do this.  Let me\ldots I don't know.  Saying `clear my conscience' sounds naive.''



``And to get this money, I have to leave this city?'' Parian asked.  She looked stunned.



``Consider it a strong encouragement.  In the end, it's your choice.  I'd appreciate it if you kept quiet about my role in your leaving, and about me giving you the money.  I think the Undersiders would understand, for the most part, but the Travelers might take issue with my interference.''



She didn't have a reply.  I glanced at Flechette but I didn't see anything in her expression.



``My employee is still on the phone,'' I reminded her.



``Oh.  Um.  What was I supposed to say, again?''



I repeated the message.



While Parian relayed it, Flechette commented, ``That's a lot of money to be giving away.''



``I have more.''  I did.  The amount I was giving Parian amounted to a little less than a third of my current holdings.  The bank account Coil had assigned to me seemed to be growing in alternating stutters and huge bounds.  The benefit of having a bank account that was managed by a guy who called himself `the Number Man', I supposed.



``Lucrative job you have there.''



I didn't reply.  It was just enough money that it'd be just a little tight to manage in the immediate future, but I felt like it wouldn't be meaningful if it didn't inconvenience me somehow.



``Okay,'' Parian said.  ``She said they'll be waiting.''



``My territory is closer to the destination than you are.  You should leave sooner than later.''



She nodded.



``This isn't some trick?'' Flechette asked.  ``Some trap you pre-arranged with those code words?''



``The code was just to inform her everything was fine.  No trap.  But I think you'll want to accompany her and the others, just to make sure they arrive safely.  There's still dangerous people on these streets.''



\emph{Would she tell me Parian could handle herself?}



Flechette turned to look at Parian, apparently considering the same thing.  ``You play dirty, Skitter.''



``All things considered, I think I've been \emph{exceedingly} fair.''



``I can't guard her and keep an eye on you at the same time.''



``That was the idea.''



``I could nail you down to the ground.  Wouldn't even be hard.  You'd have to tear your costume to shreds and run back to your territory in whatever you're wearing underneath that.''



``You could.''  I didn't point out that if she \emph{did} do that, I wouldn't have a chance of tearing my costume.



``I still think you have a warped perspective on things.  I don't think you're right.''



``I told you where the armband is.  Slater street, women's toilets, on top of the ceiling panel above the second of the three toilets.  If Dragon hasn't tracked and removed it.''



``Right.''



``Good luck,'' I told her.  ``Whatever happens.''



``We're on opposing sides, you know?  The next time we meet, we'll be fighting.''



``Doesn't mean I wish you \emph{badly}.''



``Right.''



She didn't free my armor from the floor, but she stood and joined Parian, who was already walking away.  I heard her murmuring, ``\ldotsto New York City.  I'll be finished here in two weeks\ldots''



And then they were out of earshot.  There was the sound of Ballistic continuing his rampage, tearing Dolltown to the ground.



Maybe it was good if this place was leveled to the ground.  I wasn't superstitious, I wasn't religious, but with what the Nine had done here, even their relatively short visit to this area, it felt \emph{darker}.  Wrong.  There was too much death and sadness that had occurred here.



Was that true of the city as well?  Was it better just to raze it to the ground and start anew?



I reached over slowly, wincing at the coarse sensation of metal dragging against bone and the red-hot pain of my own tearing flesh..  The movement in my shoulder had shifted the metal spike Flechette had embedded there, pulling sideways against the hole it had punched in my shoulder. I could see the blood welling out, running down into the fabric of my costume.  Once I had my hand in position, I began unstrapping the armor panel from my wrist.



Free to stand, I used my knife and some kicks to get the armor free of the floor.  Rather than pull the spike free of the flooring as I might have with a nail, I wound up pulling out a roughly cone-shaped chunk of wood, the spike and everything it had contacted seeming to have bonded together.  I picked up the armor and tucked it under one arm.



This could have gone worse.  I might have to face some ramifications if the PRT took offense to my bringing up what had happened with Armsmaster, but somehow I felt like I couldn't have let Flechette stay in the dark.  I just wasn't sure if that was for my sake or if it was for hers.  The money I'd handed away would hurt, too, but it felt necessary.



I needed medical attention, and I felt like I had to check on my territory after I'd seen Parian's.  I climbed onto Atlas.  His flight would be smoother and less jarring than walking.



I heard another crash as Ballistic continued tearing through Dolltown.  I could have notified him that Parian was gone, but\ldots no.



Maybe this wanton destruction would give him a chance to vent and find release over whatever it was that was haunting him.



I'd have to get in touch with Trickster and Genesis to arrange our visit with the Mayor for tonight.  I'd have to deal with the threat on my life, whatever form it took.



I didn't feel afraid.  Anxious?  Yes.  But not terrified, not quivering or panicking.  I wasn't sure if that was good or bad.  Grue had lamented my lack of survival instincts, not so long ago.  Had recent events worn them down even further?



I shook my head.  I'd have time for introspection later.  For now, I had to plan.





