





How the hell was I supposed to get medical assistance when the guy I was supposed to ask was looking for a covert way to murder me?



And I \emph{did} need help.  I was bleeding, for one thing.  It had only started when I'd moved my arm to unstrap my armor.  If I'd known, I would have tried to undo the straps with my bugs.



Worse, the spike had penetrated the bone of my shoulder and any movement of my arm rewarded me with scraping sensations in my shoulder socket that made my skin crawl, not to mention the pain.



I was surprised it didn't hurt more.  I hoped that wasn't a bad sign.  My fingers moved without a problem, but the lack of pain could still point to bigger problems.  Pain was a natural response, after all, and the lack of pain was unnatural.



I called Tattletale instead.



``Skitter?'' she answered.  ``How did it go?''



``Could have gone worse.  I paid Parian off, and she's leaving the city.  No blood shed, mostly.''



``Mostly?''



``Flechette was there.  I got stabbed.'' I remembered that Coil could be listening in.  ``I don't want to bother Coil with it, busy as he is.''



``Being stabbed is serious.''



``It's not too bad.  Can you lend me your medic?''



``You're just leaving Dolltown now?''



``Flying home.''



``He should be there before you arrive.  I know you two haven't gotten along in the past, but he won't trouble you.''



\emph{He won't trouble me}.  Was that her way of informing me that he was safe?  Well, I still felt better than I would be if I were putting my life in Coil's hands.



My desire to convey the \emph{image} of someone who was confident, fearless and untouchable had led to me getting impaled in the shoulder.  It was something of a weakness, but I still found myself doing it as I reached my own territory.  I landed Atlas on the beach and made my way into the storm drain, wincing every time my arm moved.  By the time I was inside, however, I was pulling myself straighter, raising my chin and squaring my shoulders.  I tried to focus on my power to remove my attention from my body.  Checking the status of the various cleanup projects, some basic reconstruction, setting up dry and clean sleeping areas, stocking up on food and medical supplies\ldots



Sierra and her little one-handed brother Bryce were there as I stepped into my lair, along with a small cluster of older kids and Tattletale's medic, Brooks.  I sat down on the stool by the kitchen counter and Brooks started examining my shoulder.



``You guys get the most interesting injuries,'' he said, in his characteristic, hard-to-place accent that seemed to put hard emphasis on syllables.



``Interesting?''



``Metal bonded to the bone.  You have some sticking through and into the cavity your socket sits in.  I have no idea how I'm going to get to the far end, cannot pull it out, and if I try sawing it off, I am not sure the shavings and flecks wouldn't do catastrophic damage over the long run.  I would say you need surgery.''



``Damn it,'' I said.  ``She probably intended for something like that, and every hospital in the area's going to be looking for someone with a spike in their shoulder.''



``I could try to handle it, but it's going to take time to get necessary tools.''



``What tools?''



``At the very minimum, a small rotary grinder, suction, some fine wire, blood\ldots''



``We have those things.''



He looked surprised.



I looked to Sierra, ``We \emph{did} get that delivery of stuff for Dr. Tegeler?''



``The dentist?  Yeah.  But it's not unpacked.''



I turned to Brooks, ``We have rotary grinders that we've been using for the cleanup, not sure how clean they'd be.  But the rest of that stuff, we've been having it delivered, so the people with medical training can start helping out.  Since we already have an able-bodied dentist, we've been setting her up.  It's kind of surprising how many people will start having issues with their teeth over just a month.''



``Okay.  Let me pack this wound and then I will need to go there.  I'll grab what I need myself.''



I waited while Brooks unpackaged and pressed bandages in place around the spike.



``How is the pain, on a scale of one to ten?''



``Ten high?  Maybe a three until I move it, then it's more like a seven.''



``I am surprised you are not passed out already.  Do you have a high pain tolerance?''



``I wouldn't have thought so.  But maybe.  Or maybe the way it bonded kept it from damaging or exposing nerve endings?''



``Maybe.  Okay.  Ginger girl, show me the stuff?''



``\emph{Ginger girl?}''  Sierra asked, archly.



Brooks smirked.



``Brooks,'' I said, ``Treat my employees with respect or I'm going to have words with Tattletale about you.''



``Yes.  I am sorry,'' he said, not sounding sorry at all.  ``Please show me where I can find the dentist's equipment.''



Sierra looked at me, and I gave her a nod as my `go ahead'.



That left me with the kids and Bryce.  I studied him.  His black hair was cut so short he was nearly bald, and like Brooks he was wearing dark gray cargo pants and a beige sleeveless t-shirt.  He'd put on some muscle since I'd seen him last.  His still-bandaged stump of a wrist tapped impatiently against his leg.



And the kids\ldots they were wearing some of the clothes I'd had shipped in, but they didn't look like the typical bunch of kids one would see around a schoolyard.  Before taking advantage of what I had to offer, they'd been eating the bare minimum, spending all of their time outdoors.  But diet and exercise weren't entirely to blame for the lack of softness in their faces or expressions.  They'd seen people they loved die.



I wasn't sure what to say.  Making small talk seemed like it would lower me to their level.



I used my power to check on progress in the area instead.  I'd had a hand in getting recovery efforts underway and ordering both tools and supplies, so I was fairly in touch with what was going on.  The streets were draining or drained in the areas we'd settled, with sandbags holding back or diverting the flooding.  Crews were filling more sandbags and loading them onto trucks at the beach.  Still others were working to clear the storm drains of blockages where they'd verified that both sides were clear of water and that the storm drains were intact.  The storm drain leading to my base had been classified unsafe for the time being, meaning I wouldn't find strangers nosing around in there.



Burned buildings were being torn down where there wasn't any hope of salvaging them, and small crews of people with the necessary skills were working to assess what could be recovered, assigning simple tasks to people who didn't have the training or know-how.  Massive tarps were going up over roofs and being tied down.



It wasn't pretty and it wasn't fantastic, but it was something.  My bugs noted a hundred and seventy people at work, one-seventy-four if I included the kids here.



\emph{One-eighty-four, }I realized\emph{. } I'd nearly missed a crew that was working beneath the streets.  The numbers were growing.



It was a little intimidating.  I didn't have any particular training or talents that really equipped me for a leadership position.  Now I was in charge of this many people.



Well, I'd do what I could.  Supply what they needed, keep an eye on things.



``Your name?'' I asked one of the oldest kids.



``Guy.''



``Sierra didn't have anything for you to do?''



``We're waiting until Char comes back,'' he said, pronouncing it `shar'. ``She said she was going to put us in charge of some younger kids, then have us run water out to the people working.''



``Good.  For now, you can run an errand for me.  Head out the door, turn right, go two blocks.  There'll be an open manhole with a cordon around it.''



``A what?''



``Tape and warning signs.  Ignore the warnings, just go to the manhole cover and shout down at them, tell them to get back to work.  I \emph{know} they're just sitting in the dark and drinking.  And tell them no power tools, now.  Not if they've got alcohol on their breath.''



``Okay.  If they don't listen to me?''



``I'll take care of that,'' I told him.



He ran off.



``Big bad supervillain, giving orders to little kids,'' Bryce commented.



Why did people insist on testing me?  Was it something about being in charge that demanded that they try to establish their dominance?  Did people like Bryce have a natural propensity for bucking authority, with me as the only clear target?  Or was it more that they were angry in general?



Either way, what did that mean for this city in the long run, if anyone who tried to change things for the better was facing this sort of resistance.



``I'm giving orders to everyone.  Everyone contributes, everyone benefits.''



``To be more specific, you're having my sister give orders to everyone while you go out and get yourself injured in fights with other capes.''



``Don't you \emph{dare},'' Sierra said, stalking back into the room.  She put down a plastic tote of medical supplies.  She sounded angry.  And \emph{scared}?  ``Do \emph{not} pick a fight with my boss.''



``I'm just saying-''



``Don't.  Don't `just say' anything.  If nothing else, she saved your life.''



``I wouldn't have needed saving if she hadn't been there,'' Bryce said.  He gave me a look that was just short of a glare.



``Don't be an idiot,'' Sierra said.  ``You were with the Merchants.''



``And things were cool.  Party all day, relax, had a girlfriend.  If she'd left things alone, I'd be okay.''



``I'm surprised Tattletale didn't mention it,'' I said.  ``The Slaughterhouse Nine eradicated the Merchants.  Barely one in twenty survived.  The ones that are left are scattered across the city.  If you'd stayed with them, you'd be dead.''



``She did mention it.  But I would have made it.''



\emph{Cocky}.  ``Then you'd be starving to death, dirty, probably sick.  Going through withdrawal, maybe.  Don't know what you were taking with them.''



He scowled, glancing at his sister.  ``None of your business.''



``Hey!''  Sierra raised her voice.  She grabbed him by the collar of his shirt, and he slapped her hand away.  She stabbed a finger into his chest, ``Treat her with respect, damn it!''



Again, that note of fear.



``I treat people with respect if they deserve it.''



``She \emph{does}.  She's \emph{saved} us, here.  That's big.''



``Wouldn't need saving if it wasn't for the people with powers being around here in the first place.''



He wasn't wrong.  As validating as it was for Sierra to stick up for me, I couldn't help but feel a pang of guilt at the idea that these circumstances \emph{were} because of capes.  Hell, if I hadn't provoked the Nine by humiliating Mannequin then this district wouldn't have come under fire by Burnscar.  There was Dolltown too, and my complicity there.  I was \emph{personally} at fault when it came to some of the damage that had been done across the city.



``You want a better reason?'' she asked.  She stepped close and pulled him down to hiss words in his ear.  She wasn't being as quiet as she seemed to think she was, trying to hide her words from me and the kids.  ``\ldotsthey attacked me and Char\ldots \emph{mauled} them\ldots  \emph{Mannequin\ldots}''



I shifted positions, and Sierra must have seen it, because she lowered her voice to an inaudible hush as she finished.



Rattling off a list of the things she'd seen me do.  Reasons that gave her cause to be \emph{spooked} if her brother was mouthing off to me.



When we'd met, Sierra had commented that I wasn't what she'd expected from a supervillain.  Somewhere along the line, I'd painted a different picture.  She clearly had no trouble with me on a day-to-day basis, but she also knew that when I was pushed\ldots well, I'd gone easy on the three ABB members that had attacked her and Charlotte, but that was only in a matter of speaking.  I'd still left them fleeing in mortal terror.



Bryce looked at me and I could see him give me a once-over glance, as if assessing me in a new light.



``Go help Brooks,'' I told him.  ``I'll direct you to him with my swarm.''



It took him a second to weigh whether he wanted to or not, but he did turn and step out the front door, following the thin trail of bugs that I was gathering between him and the warehouse we were keeping supplies.



``Want me to go, too?'' Sierra asked.



``Your choice.  Might be better to give him space.''



``I keep having to do that.  When do we start being a family again?''



\emph{I'm not the person to answer that question.}



``If you decide to leave him be, I could use a hand collecting some things so I can make effective use of my time.''



``Okay,'' she said.  She seemed to pull herself together a bit.  ``What do you need?''



``My laptop from my room, and the surveillance stuff from the cellar.  There's another set of surveillance gear in the bag beneath the shelves.''



Sierra hurried off to gather the equipment.



The ensuing minutes were a little disorganized, as Bryce and Brooks both arrived with the last of the medical equipment.



``Blood type?''



``AB.''



He took one bag of blood out of the box and placed it on the counter.  ``Want to do this in your room?''



``I have an armchair on the second floor I could sit in.''



``Need you reclining.''



``I have somewhere to be tonight,'' I told him.  \emph{Though this would be something of an excuse to avoid the kill}.  ``Don't put me under.''



``This is going to hurt.''



I had another reason for not wanting to be put under.  I wanted to keep an eye on him.  My conversation with Tattletale had suggested he wasn't a threat, but I'd feel a heck of a lot better if I could verify that for myself.



``Do you have local anesthetic?'' I asked.



``Yes.''  He tapped one finger on a tiny bottle.  Lidocaine.  I recognized the name.  ``But will not prevent all pain.  I do not want to use too much.''



``We'll try that, then.''



We headed up to the second level and I settled into my chair.  For additional lighting, I had my `switch beetle' flick the concealed switch that was contained in his terrarium.  They lit up as I settled in.



Brooks hooked up the blood bag but left the tube hanging, unconnected.  Other supplies were arranged on the table he'd had Bryce bring up.  He seemed very particular about the order and what was being kept



``For a field medic you seem pretty well versed in this stuff.''



``Worked in many hospitals,'' he replied.  ``Many places.  Often with less than this.  Sometimes with more.''



``Okay.''



``We will have to dislocate your shoulder to access the inside of shoulder socket.''



``Okay.''



``You will take muscle relaxant to minimize damage from dislocation.  You will need to exercise arm to prevent more dislocations.''



I didn't like the sound of that, the possibility that it was actually poison, but the muscle relaxant came from the bottle, and they had the brand logo etched into them.  One potential danger averted.  No way he'd arranged it this quickly.



``I can do that.''  I took the pills with a swig from the offered bottle of water.



Sierra arrived with the laptop and a large bag.  She handed me the laptop and then plugged it in beneath one of the lower shelves.  I balanced it on my armrest, turning sideways so I was sitting with my bad shoulder facing out front, my legs curled around me for as much stability as I could hope for.  Sierra began arranging towels and plastic cloth around the chair.



``This would be easier if you just lay down,'' Bryce said.  I saw Sierra scowl at him.



``It is fine,'' Brooks said.  He lifted my arm and let it flop back down.  I tried not to react to the pain that elicited.  ``Only one that suffers is her.''



``Ever a charmer, Brooks,'' I commented, but my attention was on the laptop.  I used the switch beetle to open all of the terrariums, and withdrew collections of spiders, dragonflies, large moths and roaches.



``They should not touch chair,'' Brooks said.  ``Or anything on table.  Must keep everything as sterile as we can.''



``I know,'' I said.



I gathered the components from the bag, using my bugs to draw them out and airlift the miniature cameras, microphones and transmitters into the air.  One by one, I turned them on and used the laptop to connect to them.  I used my free hand to click through each camera in turn, making their feeds the focus of the main window.



Using my bugs, I drew forms around each, vaguely humanoid.  It wasn't as intuitive as I was forced to use my own eyes to assess the accuracy.  Still, I managed to rearrange each until they vaguely resembled me.  I marched them down the stairs.



``Outside end first,'' Brooks said, starting up the rotary saw.



Not my favorite sound.  And the sensation of it sawing at the metal, it brought back even more unpleasant memories.  Being on my back, Bonesaw trying to cut a hole through my skull\ldots



I shivered.



``Don't move,'' Brooks said.



I focused on my swarm-clones, staying totally still while he worked on removing the metal end of the dart.  They were largely composed of flying bugs, but I was bulking each of the forms out as more bugs arrived, giving them a more solid mass.  I used my free hand to pop my ear-buds in.



I felt bad about leaving my territory as often as I had been.  People were spooked, scared and insecure.  Having a leadership figure that was never around wasn't helping matters.



This would, I hoped, establish a kind of \emph{presence} that had been lacking.



Sierra had been coordinating everyone, trying to put people with experience in charge of people who were lacking it.  It was interesting, trying to hold multiple conversations at once with the various project leaders.  Difficult, too.  For one thing, my speech with my swarms was somewhat lacking, missing consonants, but I could still make myself more or less understood.  For another, my ears could only process one thing at a time.  I managed by talking with one or more swarm-clone while listening with one at a time.  After too many misfires and moments of confusion, I scaled down my efforts to a single conversation at once, simply standing silently by with my other selves.



I made a mental note to try to practice with that.  Exercising the range of my power hadn't done anything for me, and there didn't seem to be any upper limits to how many bugs I could control at once, but there had to be other ways I could train my abilities.  Multitasking was one I hadn't tried yet.  Trying to interpret the senses of my bugs was another, though I feared it would take a more concerted effort to effect any sort of change.



When Charlotte returned, I was in the middle of helping a foreman with the layout of a building, using spiders to draw out a loose web in the general shape of the planned shelter, lifting bits of wood to make the lines more visible from a distance.  I adjusted the threads as required to meet his needs.  Charlotte climbed out of a truck with five more of my people and made a beeline to my swarm-clone.  \emph{One hundred and}\emph{ninety people working for me}.



Word was apparently getting out about this being a safe haven.



My conversation with her was delayed as Brooks enlisted Bryce in twisting and pulling on my arm while Brooks held my neck and torso.  Bryce drove his elbow against my shoulder while it was being twisted to its absolute limits, effectively knocking my arm out of its socket.



I managed to avoid making any noise beyond a guttural grunt, then took a few seconds to try to avoid blacking out from the pain.



As heavily as I was breathing, back in my lair, my swarm-people didn't show any sign.  I focused the whole of my attention on them, as if I could remove my consciousness from my real body.



``Any problems?''  I asked Charlotte, once I'd recovered enough to pay attention.  Glancing at my shoulder, I could see Brooks making an incision in the skin of my shoulder.  He'd managed to open the tear in my costume.  I hadn't been paying attention to how.  I deliberately looked away as Brooks tried to forge a path  to the inside of my shoulder socket.



``Not sure,'' Charlotte said.  ``Have a look.''



It was Parian.  I'd been so focused on my shoulder, the three-dimensional web-blueprint and my swarm-selves that I hadn't noticed her getting out of the truck.



``You didn't leave,'' I said, when she'd joined Charlotte and my swarm-clone.



``I didn't think the money would be real,'' she responded.



``Of course it was.''



``It's\ldots it was a lot of money.  Very generous.  But we were talking about it, and split between us, it's not enough to give everyone all the care they need.  I told them to go ahead, that I didn't need a share.''



``Sorry.  I was worried it wouldn't be enough,'' I said.  ``Are you saying you want more money?  I might have to say no.  There's a limit to what I can spare.''



``No!  No.''  She hugged her arms to her body, looking around at the people who were working.  ``Just\ldots I thought maybe I should hear you out.''



``Okay,'' I responded.



``Except it's not really you?''



My clone shook her head.



``Can I talk with the real you?''



``I'm in my lair, and I'm preoccupied.  You'll understand if I don't reveal the location, given who your friends are?''



``Yeah,'' she said.  She was still looking around, watching as a group moved by, pushing wheelbarrows of burned wood.  ``I\ldots I was telling myself that there was no point to taking your offer, that I could use my power and make more money legitimately.  But that's not true at all, is it?''



``Walk with me?'' I asked.



She nodded.



I led the way through my territory with my clone as I talked.  ``Crime \emph{does} pay.  I made the offer to you because I thought it would be the best way to get your Dolltown residents the money they needed to get their old lives back.  Or get as close to their old lives as possible.''



``I kind of hate you,'' she said.



``Why?''



``You're making it out like I'm a bad person because I won't betray Flechette and my own moral code to help them.''



``I don't blame you for your decision.  I don't think any less of you.''



``But you wouldn't make the choice I'm making.''



``No.  I didn't.''



``And you've done more to help my people than I have.''



``You've protected them to the best of your ability through this city's darkest hours.''



``You really think we're past that?  The bad days?''



``Yes.''



I winced as the grinding resumed, this time inside my shoulder socket.  A makeshift rigging inside the cavity caught the metal shavings, while Bryce held the tube to suction the metal shavings out.  So far, no assassination attempts.  Good.



``I don't know what to do,'' Parian admitted.  ``This is\ldots seeing it makes me wish I'd done something like it.''



``I'm not going to push you towards one choice or another.''



``I know.  You made that clear when you gave me the money with no strings attached.''



``Look,'' I said.  ``I know Flechette was saying my perspective is warped, but I think the system\ldots you know, \emph{society, }it's like a series of rules and expectations that we established under some general expectations.  But recent events have made it pretty clear that those expectations, those assumptions, they might not apply.''



``Because of us?  Capes?''



``Yeah.  At the end of the day, barring some extreme examples like powerful dictators, there's always the fact that any bad person who doesn't have powers can be killed with a gun, a knife, or even a good punch in the right place.  That's not the case with us parahumans.  The balance of power is pretty damned off-kilter.  Things aren't \emph{fair}.''



``Are you making that imbalance better or worse?''



``I'm\ldots addressing the problem.  I'm saying there's no point to trying to hold on to the old status quo when it's based on a foundation that no longer exists.''



``So you're going to take over the city.''



``Yes.  Because at least for right now, I can give these people what they need.''



I moved my clone's `head' and followed a group of kids who were running away from my lair, carrying six-packs of water bottles.



``And later?''



``I don't know.''



We walked in silence, past a bonfire where scrap wood was being burned.  Brooks and Bryce, meanwhile, set to shoving my arm back into its socket.  All of the ambient pain disappeared in an instant.



Parian needed the money, she needed the assurance that she could help the people she'd failed.  I understood that.



``I can offer you one last compromise,'' I said.



``What?''



``I can't guarantee it'll work, I can't say if anyone else will accept the proposal, and I don't know what's going to happen long-term, but we don't have to call you a member of our team.  We don't have to call you a villain.''



``But I'd take territory for myself anyways?''



``Yes.''



``Others would call me a villain, just because I wasn't fighting you guys.  They'd know I was cooperating with you.''



``Not necessarily.  Maybe the people in charge, the Protectorate and Wards, maybe they'd understand it, but the people on the ground level wouldn't.''



``The media would out me.''



``I think we control the media.  Or enough to throw some doubt into the mix.  The rules are pretty simple.  You take territory, you hold it, and you ensure that there's no crime or parahumans operating there without your consent.''



``And Flechette-''



``I don't know her.  I can't say how she'll react, but maybe if you explain nicely, maybe if you frame it right, you could convince her it's for the greater good.  So long as she convinced the other heroes to leave your territory alone, let you enforce the law there all by yourself, you wouldn't have to fight them.''



``And if she didn't-''



``That's up to her.  Or you.''



She stared around my territory.  It wasn't pretty, there was still devastation everywhere, but things were getting better.  It was maybe the only place in the city where things were improving as fast as they were.  We weren't taking two steps forward and one step back.  It was all forward momentum.  Not even a week had passed, admittedly, but it was progress.  And it was apparent.



``I don't think I could accept if Flechette doesn't agree.''



``Okay.''  The alternative was unspoken.  \emph{If she does}\ldots



``I hate you,'' Parian said, and it was answer enough.



Brooks was finishing stitching up the incision in my shoulder.  I already had two pieces of scrap spider silk at the ready – one to cover the hole in my costume and another to serve as a sling until my shoulder was stronger.  If I adjusted my cape, I could cover the arm so the injury wasn't too obvious.  I stood from the chair and stretched, then reached for my cell phone.



``I can live with that,'' I told her, speaking through my swarm-clone.  I clicked through my contact list and called the man who was plotting to kill me.





