





The benefit of using my swarm-clone to communicate with Parian was that I had relative privacy to talk to Coil.  He picked up on the fourth ring.  Not quite so prompt as Tattletale tended to be.



``Skitter.''



``I know you wanted me to use Ms. Cranston instead of calling you, but this is sort of important.''



``I'm listening.''



``I've talked with Parian, and we've come to a tentative agreement.  She'll need to talk to other people before making a decision, but I think she'd join our alliance.''



``I see.''



There was a long pause.  I was getting ready to speak and ask if he was still there when he spoke once again.



``What are her terms?''



``She holds territory, she'll defend it against all comers, but she's not going to do jobs or do anything criminal.  As far as anyone else is concerned, she's not a part of our takeover.''



``The implication being that we're too weak to deal with her.''



``That wasn't exactly what I had in mind.''



``It's the conclusion others will come to.''



I felt a swell of frustration and anger, powerful enough that I might have snapped at him if I could have come up with what to say any faster.  I had to remind myself that I was anxious over the hit Coil had put on my head, and I felt betrayed.  I recognized that it was stupid to feel betrayed by Coil when I was actively planning to fight him if he didn't cooperate on the Dinah front, but I \emph{also} knew I didn't tend to handle it well when someone I'd trusted stabbed me in the back.



Not that I'd ever \emph{trusted }Coil but\ldots



Okay, I wasn't sure what I was thinking on that front.



I forced myself to calm down before saying, ``I'm sure there's a compromise.  Will you talk to her?''



``I will not risk revealing my identity, no,'' Coil said.



\emph{Damn him}.



``But,'' he continued, ``I will speak to her through a liason.''



``Thank you.''



``Though this could have been done more smoothly, I do appreciate your hard work.''



\emph{This from my would-be murderer}.



``It's not a problem.  Ballistic might be upset if he realizes I went behind his back on this, so maybe if anyone asks, she got spooked and came to you?''



``Perhaps.  I'll be discreet, in any event.  It wouldn't do to have friction between your two groups.''



``Right.''



``Speaking of inter-group relations, I believe Trickster is preparing to leave for the mission this evening.  You'll want to contact him to arrange something.''



I'd been hoping to put this off.  It still felt like yesterday that I was watching my back every moment, waiting for an attack from any corner.  I wasn't eager to return to that state.



``Okay,'' I said.



He hung up without another word.



Parian first.



``I've raised the subject with others.  They'll be in touch.  You should talk to Flechette and decide where you stand before then.''



``A lot of pressure.''



\emph{I don't think you understand real pressure,} I thought.  But I didn't say it out loud.



``Yeah,'' my swarm said.  The drones and buzzes that made up the syllables helped mask the lack of real sympathy.  I began working to use silk strands and flying bugs to lift a cell phone into the air.  I thumbed through the keypad and sent a text to Ms. Cranston to inform her about what I was doing.  ``I'm flying a phone to you, it'll be in your hands before you're out of my territory.  Someone will use it to call you before the end of the day.''



``This is you subtly telling me to leave?''



``I'm in the middle of something, yes.  Thank you for hearing me out.''



``It was the least I could do, after the help you've offered my friends and family.''



``Whatever you decide, take care of yourself, Parian.''



``You too.''



I scattered the swarm, then paused to think.



The painkiller was starting to wear off, and I could feel the steady ache in my shoulder.  I still had a dart sticking through the bone.  Brooks had only removed the points on either end.  I could only hope the pain kept me sharp.



I'd hoped to take a break and formulate some strategy, some plan.  I had a few small ideas, but they weren't broad enough to cover every base.  And there were a lot of bases to cover when someone as well equipped as Coil was after me.



\emph{Fuck}.



I couldn't do up all of the armor I'd removed with the one hand, so I enlisted Atlas' help in putting the armor on my injured shoulder, using his forelimbs to hold things steady.



I took a deep breath.  It wasn't confirmed one-hundred percent, but I had my suspicions that Parian was on board.  I didn't want to die, exactly, I was prepared to fight tooth and nail to avoid it, but at the same time I was \emph{ready }to die, now.



I didn't really have friends, outside the team.  My teammates would miss me, but they'd recover in time.  Death was a reality in our business.



My dad hadn't heard from me in some time.  If I died, well, perhaps not as great a shock as it might otherwise be.  I knew it would hit him as hard as my mom's death had, that he'd be devastated\ldots but again, he'd recover.  Maybe it would be easier, because at least here he'd have someone to blame, the city, the thugs, whoever Lisa told him was at fault for my murder.  I was pretty sure she wouldn't reveal my identity to him when a simpler, to-the-point explanation would do.



And my people?  My territory?



I felt Parian receive the cell phone, a few blocks away, pulling it to her hand with telekinesis.  From the bugs that lingered on it, I could feel it vibrate pretty violently as it moved the short distance through the air.



If I died, Parian could take over my territory.  I had the feeling I could trust her to care about my people the same way I did, more than I could trust even my friends.  The transition wouldn't be too difficult.



I took in another deep breath, then sighed.  \emph{For Dinah}.  In any other circumstance, I'd back down, leave Coil's employ.  But I was willing to brave this if it meant keeping her and her freedom in my reach.



I dialed Trickster.



\sectionbreak



Atlas carried me into the nice part of town, southwest of the Towers.  The Christian private school wasn't far from here.  Immaculata.  New Wave was also based here.  I kind of hoped I didn't cross paths with them.  If they shared any of Flechette's opinions about me being at least partially to blame for whatever had happened with Panacea and Glory Girl, well, they'd be even less inclined to hold back.



I needed to find out the story there.  Had to ask Tattletale, when I had a free moment.



The area was riddled with hills and glades, with ridiculously large houses gathered in small neighborhoods.  Brockton Bay tended to zig-zag pretty drastically between the poverty-stricken areas and the wealthy.  The contrast seemed even greater here where things were largely untouched by Leviathan's attack, compared to the rest of the city where streets sat under inches of water.



I didn't join Trickster and Genesis.  Instead, I set Atlas down in one of the wooded glades close to my destination, glanced at my phone to ensure I'd followed directions to the right spot, and then got my laptop out to prepare.  I was a little early, which meant I could afford to take the time to prepare.



The range would be lower with the trees and any buildings between me and my destination, but I was still better off using my swarm-clone as a body double.  I double checked my equipment and weapons while I waited for my `clones' to gather together.



Centipedes and bugs chained end-to-end for the hair.  Larger bugs formed the bulk of the legs, torso, and the core of the head.  Smaller bugs filled the gaps, while flying insects clustering together to form the arms and the parts too unwieldy to be supported by the rest, like the face.  Once the basic form was there, it was just a question of refining it so the general silhouette was right, and positioning the miniature camera and microphones so they had eyes and ears I could use.



Once they were ready, I gathered one swarm on top of Atlas and flew it to Trickster and Genesis.  I walked with my swarms at my side, my laptop open and held with my good arm so I could see the video feed.  As I gathered more bugs on top of my costume and in my hair to make myself resemble the clones, I used stray bugs to form similar laptops for the other clones.  They didn't have glowing screens, but the generally rectangular shapes would serve for anyone looking at a distance.



If `I' was in immediate danger, my clone on Atlas' back would take the hit.  If my enemy or enemies saw through the ruse and came looking for me, they'd have to pick me apart from my clones.  That meant they would have to take the time to find a telltale clue, they'd have to guess with only a one-in-four chance of hitting the real me or they'd have to spread their attacks out among each of my clones.  I had the additional security of bugs filling the area, sweeping over surfaces and ledges to spot anyone who might be in place to stalk or snipe me, and my costume served as a final line of defense.



Redundancies.  It didn't feel like enough.



Trickster and Genesis were waiting as Atlas descended.  They were crouched with their backs to a stone wall that bordered one property at the edge of a hill.  Trickster was holding binoculars, gazing down at the neighborhood below us.  Genesis was in the form of a ghostly woman wreathed with chains.  Her white hair was smoky, wispy, and covered her face, and her fingers were talons.  She had no lower body extending from the tattered poncho-style cloak she wore, and simply floated as though she were as light as air.  How had she done that?  Some basic flight mechanism?  A gas balloon in her stomach?



\emph{So powerful}.



``Welcome.  Have a look,'' Trickster said.  He extended one hand with the binoculars.  Binoculars I couldn't use with my camera.



``Don't need them.  Which property?''



He pointed.  It took me a second to relate the direction his arm was pointing with the camera angle and relate that to my own position relative to my clone.  I could have figured it out in an instant if I'd put a bug on his hand, but I didn't want to clue him in if I didn't have to.



The grounds of the building he was pointing to was nearly as large as the city block where I'd grown up and lived until a couple of months ago.  There was a fence, but it seemed to be directed at keeping the family's dogs in rather than keeping intruders out.  Chain link, no barbed wire.  I knew he had dogs from the flies that were clustered on the feces in the back yard that hadn't been picked up, and the larval young that festooned each clump.



Not too many bugs inside the house.  There were some in the walls, but the home seemed relatively new, and the insulation was packed tightly enough that nothing was really living in the walls.



It took me a minute, but I did manage to start a headcount.



``There's guards?''



``There's a police presence in this area.  I think they're expecting trouble,'' Trickster said.  ``Anyways, the reason we're here at this time and place is that the mayor \emph{always} eats dinner with his family.  Tattletale says he's only missed three meals in twenty years, and that was only because he was out of town for work.  His planned trip to Washington is going to be his fourth time away from home, so this is the one place we can be absolutely sure we'll cross paths with him.''



I found the dining room and started counting the number of shoes under the table.  ``Four adults.  I think two male, two female, judging by the footwear.  Two younger girls. Going by their size, I'd guess between eight and twelve.''



``He has a son and two twin daughters,'' Trickster said.



I arranged bugs on the ground by Trickster to sketch out a rough floor plan of the house and show the pair where the family was relative to us.



``How do you want to do this?'' Genesis asked.



``We scare the wits out of them, then we'll introduce ourselves to the mayor,'' Trickster said.  ``You guys start us off.  I'll keep an eye out for trouble and handle things if any cops show up or if anyone flees.''



``We're attacking with their family there?'' I asked.



``Sure.  Bigger impact if we threaten them too.''



``Not sure I like that.''



``When I was talking to Coil about what Tattletale said about the schedule, he suggested it.  Unless you want to go against him?''



\emph{He was talking to Coil.  }I made a mental note of that.  Did I need to watch out for an attack from Trickster?  It would be as simple as swapping the positions of an active grenade with a stone near me.



It was possible.  He was ruthless, he didn't seem to have many compunctions about killing and he was in the best position to do it.  I couldn't sense any people who might be Coil's soldiers.



There was the possibility that I was walking into a trap, that everyone in the house we were about to attack was a threat.  I could handle that much.



Too many potential avenues of attack.  Too many potential threats.  And with the possibility of long-range weapons, Trickster or even a surprise attack by Genesis, it could come at any instant.



``Skitter?''  Genesis asked.



``Hm?  Right.  Um.  I suppose not.  We just scare them, right?  We don't do any physical harm?''



``Right,'' Trickster said.



Well, I could do that.  It wasn't so different from what I'd done in my first job with the Undersiders.  I'd terrorized hostages then for a greater purpose, and I could do the same with a family for the same reason.



``Just give me a second,'' I said.



``I'm going, then,'' Genesis said, floating over the edge of the hill.



``Not the first time you've needed time to get ready,'' Trickster commented to me.



``Hm?''



``Just seems like a drawback.''



\emph{Is he threatening me?  Letting me know he's on to one of my weaknesses?}



``I'm a general, and it takes time to mobilize my army.  Better to hit hard with all my forces at once.''



``Not always.  You could have built up to a crescendo there.''



``And give them a chance to scatter?  I'd have to divide the swarm to cut each group of people off, which would mean less bugs for each, smaller effect overall.''



He shook his head.



``What?''



``Nothing.''



``You seem just a \emph{little} more hostile than before,'' I said.



``Do I?''



My bugs had gathered around the handful of entry points I'd been able to find.  Windows were open, but each window had been set up with either plywood or screens to compensate for the glass Shatterbird had destroyed.  There was a fan system for the bathrooms that was structured to discourage bugs from crawling through in reverse, with flaps that would presumably only open when the fan was active, and that was easy to bypass with some cooperation of the arthropodic collective.



``Yeah.  Any reason for it?''



``Not a huge fan of you stepping on Ballistic's toes.  He's sort of a friend.''



\emph{Not the way he tells it}.  ``I didn't intend any offense.''



More bugs were entering through one of the doors at the side of the house, which was ajar.  I presumed it was to let the warm late-spring/early-summer air flow through the house.  The challenge there was keeping the bugs from being spotted before I was ready.



When I realized what Genesis was planning, I shifted my bugs to follow.  She headed straight for the kitchen window and crashed through the plywood there.  She was followed shortly after by my swarm, spilling into the room to spread over windows, ceiling and floor, only a small few darting around the people.



They turned to run, naturally, running for the door that led to the kitchen and to the hallway.  They were met by the remainder of my swarm, a thick cloud of flies, dragonflies, moths, roaches and beetles.  I could feel them backing away, four adults, two children.



``Police are on their way.  Gonna swap them with us the second they get to the house.  Warning you in advance so we can look confident.''



\emph{Damn}.



``Appreciate that line of thinking, but there's one small problem,'' I said.



He looked at me, then frowned.  ``I can't get a grip on you.  You're doing what you did when you were talking to Legend and Miss Militia.''



``A little more refined than that, but yeah.''



``Fuck,'' he said.  Then he groaned. ``And now I've lost sight of the cops.''



``I can deal with them, if you want.''



``Just find them and I'll handle that.  Where's your real body?''



I hesitated.  Then I had my clone turn and point to another clone.  Just in case he decided to go on the attack.



``I see you.  Right.  And the cops?''



``Over there, but don't teleport me,'' I said.  ``I've got something else in mind, and the visual effect will be stronger.''



``If I don't teleport you, I have to fight whichever cop I'm not teleporting,'' he noted.



\emph{Cope}, I thought.  I deigned not to respond, and dismantled the clone that was standing next to him.  I did draw an arrow pointing him to where the two officers had circled one corner of the property.



Rather than visit the house myself, I gathered some of the bugs I'd sent to the room and began forming a clone there.  From what I'd seen of the process, it was sort of spooky in its own right.  A person materializing from vermin.  I carried the small camera and microphone towards the swarm, using the video feed to remotely see the clone from a short distance so I could match the finer features and body shape.  When I was done, I added the remaining bugs to the swarm, the camera and microphone hidden in their midst, and shifted the camera into place.



I recognized our mayor.  Never someone I'd paid a whole lot of attention to, given how I wasn't exactly a voter, but I recognized him in a general way.  His face tended to pop up in advertisements and media.  If the city wasn't in the state it was in right now, it would be on every TV channel, well into the swing of things for the imminent mayoral elections.  He was fifty or sixty, with horseshoe-pattern baldness on a round head and large ears that sort of stuck out.



The woman next to him would be his wife.  She had the look of someone who had purchased their good looks, with stylish clothes, an expensive haircut and top-notch makeup and skin care.  She was clutching her husband, who was holding his two twin daughters.



There were two young adults there too.  Older teenagers or young twenty-somethings.  The guy looked seriously well-built, the girl statuesque;  I got the vibe of an athlete and his cheerleader girlfriend more than I got the impression of a brother and sister with good genetics.  The guy stood a little in front of his parents and girlfriend, as if he wanted to protect them.  Genesis and I stood on the other side of the dining room table.



``What do you want?'' he asked.



``A conversation,'' Trickster spoke.  He had hopped up to the ledge of the ground-floor window and was now hopping down, one hand on his hat.  He adjusted it.  ``Hello, Mr. Mayor.''



The mayor looked at each of us in turn.  Well, at Trickster and the fake-selves that Genesis and I were producing.  ``To what do I owe this questionable pleasure?''



``We hear you're going to Washington tomorrow.''



I saw the son turn to look over his shoulder at his dad.  I also noted that he was discreetly drawing a phone from his pocket, concealed by the way he'd turned his body.  If I couldn't sense movements through my bugs, I would have missed it.



I could have said something, but I stayed quiet.  Instead, I drew Atlas to a point near the window and began uncoiling and stretching out the lines of pre-prepared silk I'd already drawn out for emergency use.



``I am.''



``Well, I think it would only be fair if you heard from \emph{all} of your constituents,'' Trickster remarked.  ``Before you come to a decision.''



``You pay taxes?'' The son asked, shifting his position again so his right hand was hidden behind his girlfriend.  I could feel him adjusting his grip on the phone.  As far as I could tell, he hadn't actually done anything to it.  I waited for him to stop moving his hand, and then threaded a series of flying bugs between his fingers and the device, winding the thread around it.



``Rory,'' the mayor spoke, his tone a warning.  He turned his attention to Trickster.  ``And?  Which outcome are you hoping for?''



``I think it would be \emph{excellent} if the city kept on going.  Things are getting better.''



``And you're putting yourselves in charge,'' the mayor noted.



``We're just keeping the peace,'' Trickster said.  ``Doing a better job than your local heroes.''



``If you have a liberal interpretation of `peace', maybe,'' the mayor said.



Rory moved his fingers, tapping the screen, and I had Atlas fly away from the window.  The phone was torn from his hand and bounced off of the window pane before landing outside.  Atlas reeled it in further while Rory looked around in confusion and alarm.



``No phone calls,'' I spoke, buzzing through my swarm.



``Give that back,'' he said.



``Is your phone really a priority?'' Trickster asked.



``Yeah,'' Rory said.  ``Yeah it is.''



``Then you should have known better than to use it here,'' Trickster said, shrugging.



``\emph{Give it back,'' }Rory turned to glare at `me'.  At my swarm-double.



Trickster chuckled, ``Never really got that smartphone craze.  People go gaga over the things.''



\emph{No,} I thought.  \emph{Something's off}.



What I wouldn't give for Tattletale's power.  Or even to have her present.  How would she pull the pieces together, fill in the blanks?  She could have looked at the big picture here and known \emph{exactly} what was going on, while I was left to guess.



The obsession over the phone?  I couldn't draw any conclusions.  What else?  The family dinner with the son bringing his girlfriend over?  Nothing too strange.



They weren't scared.



The little girls were glaring at us as they clutched their dad, Rory was too focused on his phone when his family was in imminent danger, and Rory's girlfriend was staying very still.  Topping it off, the mayor was too casual in how he was addressing us.



\emph{Ah.}



``I think it would be in \emph{everyone}\emph{`s} best interests if Brockton Bay kept going.  Not quite fair to judge the fate of the city at its lowest point,'' Trickster said.



``Are you being ironic on purpose?'' The mayor asked.  ``You're making a very strong case for why the city \emph{shouldn't} continue down the path it's been going down, just by being here.''



Again, that confidence.  One didn't trade banter with someone who was implicitly threatening them and their family with bodily harm.  Not if they didn't have some measure of security their would-be assailants weren't aware of.



I considered the various possibilities.  Not too hard to narrow down the options, with the process of elimination.



I drew the words against the wall, above and behind the gathered family.



Trickster didn't seem to notice.  ``I'm surprised you aren't showing us more respect.  You'd think we'd almost be equal on a level, current guy in charge of the city talking to the aspiring rulers.''



``I earned my position through hard work, dedication and by convincing the people that it was in their best interests to vote for me.  Which it was.  You three?  You're criminals.  Thugs.  You didn't earn anything.''



``\emph{Thugs}?  Do Thugs take on the Slaughterhouse Nine and walk away?''



``All you have going for you is violence and intimidation.  You can't accomplish anything but destruction that way.''



I made the words on the wall bigger.  Trickster didn't see them, or he didn't care.



``Trickster--'' I started, speaking through my swarm.  \emph{I need to have a word with you}.



``Well,'' Trickster said, cutting me off, ``If you insist, who am I to argue?''



In an instant, one of the two twin girls was replaced by one of the dining room chairs on our side of the table, and vice versa.  Trickster grabbed her hair and pulled her close, drawing a gun and pressing it to her head.



``Trickster,'' Genesis said, in the same second I moved forward to stop him.



Was she trying to stop him as well, or had she seen the words?



She settled one talon on his shoulder.  I wasn't sure what signal she gave, but Trickster paused.



Whatever it was, he must have looked up at the words I'd written, because Rory noticed.  He whipped his head around to see, and I couldn't disperse the bugs fast enough.



`Triumph' written on the wall with bugs with a triangle beneath, pointing at his head.  Above his `girlfriend' were the words `Prism or Ursa'.



The mayor's son was the civilian identity of Triumph.  Enhanced physical prowess and a concussive shout that could punch holes through concrete.



He whipped his head around and stared at Trickster.  Before the teleporter could pull the trigger or do anything else, Triumph \emph{shouted}.  His sister was untouched, but Trickster was sent flying into the wall hard enough that he was half-buried in the drywall.



``Duck, Kyla!''



The little girl threw herself to the ground as Triumph lunged forward, kicking the dining room table.  It slid halfway across the room, over `Kyla' and into the wall. The side slammed into Trickster's midsection, and the table's contents flew into the villain and the wall around him.  Trickster went limp, his upper body flopping over the table.



I mobilized the swarm, but Triumph was already shouting again, slamming Genesis into a wall, much as he'd done with Trickster.  A third bellow annihilated my swarm-clone, and he turned to start eradicating my spread out bugs while his family ran for the hallway, led by the superheroine.



Couldn't get a serious number of bugs together in one place to mount a serious attack without Triumph obliterating them and he was either too angry or too stubborn to surrender to the stings and bites I \emph{was} managing to inflict.  The superheroine had her phone out and I wasn't able to tug it from her hand like I had with Triumph's.  They would be getting reinforcements shortly.  Even if I took all of them out of action, I'd still have to get Trickster out of there and escape with my own hide intact.



``Damn it,'' I cursed.  I broke into a run, accompanied by my swarm-doubles, hurrying for the house.  I couldn't leave him there, not without jeopardizing everything.  He struck me as being disloyal enough to offer information for his own sake, or information about the \emph{Undersiders, }at the very least\emph{.  }And leaving him behind would leave a permanent rift between our team and the Travelers.  It could even mean being dropped by Coil, an excuse for him to separate me from my teammates.



That said, I couldn't save him or mount a serious attack with just my doubles.  He was hitting too hard, handling my bugs too effectively.  I could have killed or critically injured his family with the few bugs I \emph{did} have, brought them down with the more dangerous insects, but I wasn't willing to go that far.  Not with people who didn't deserve it.



Atlas wouldn't be strong or versatile enough to carry an unconscious body to safety.  If I was going to haul Trickster out of there, it would have to be with my own two hands.



I could only pray I wasn't exposing myself to whatever assassination ploy Coil had in mind.  Or worse, that I wasn't doing \emph{exactly} what he wanted me to do.





