





I had two different heroes to deal with, one of whom I couldn't identify yet.  That posed something of a problem: each likely possibility for the heroine's identity made for a very different scenario in how this fight could play out.



Process of elimination had told me that Rory would be one of the local heroes, because there weren't any prominent male villains who I couldn't identify with their masks off; Coil had outed Empire Eighty-Eight, which had split into the Chosen and the Pure and everyone else had been eliminated or driven out of the city.  I'd identified him as Triumph from his build.  Assault and Cache weren't as muscular, the Wards were younger and smaller, and the remainder of local heroes were women.  That had been easy enough once I'd pegged him as a cape.



His `girlfriend' was harder to pin down, both as a cape and in terms of her costumed identity.  I'd read her confidence and judged that she wasn't terrified enough to be ignorant about Rory's secret.  She probably wasn't a civilian in the know, either, because she hadn't been cowering behind Rory.



Going by her appearance, I didn't think she could be Miss Militia or Battery.  Her blonde hair didn't fit, for one thing, and she was too tall, too muscular.  She had to be one of the two female capes who came to Brockton Bay with Legend.  It was critical that I figure out which of the two she was before getting into a fight with her.  Prism was a duplicator who could consolidate into one body to get a temporary boost in strength, speed and durability.  Maybe other areas too.  Fighting her would mean staying out of close-quarters combat at any cost.



Ursa Aurora, by contrast, summoned ghostly `bears' onto the battlefield.  On a level, she'd want to fight like I preferred to, relying on her minions while staying out of the thick of things.



Two possibilities, each requiring very different tactics to handle.



I set my bugs on her and her alone in the hopes of forcing her hand.  Atlas had returned to my side, and I made sure to collect Triumph's phone before climbing on.



Triumph had picked up Trickster's limp body and was mounting a fighting retreat in the direction the heroine and his family had gone.  He shouted again and again, controlling the magnitude, force and breadth of each strike to hit the maximum number of bugs with just enough force that he was killing or crippling them without destroying the house.



Walls of bugs pressed against the exits of the house.  If they escaped before I got there, I wasn't sure I'd catch up.  Triumph would be able to run faster than I could, Ursa Aurora could presumably ride her bears like Bitch rode her dogs, and Prism had the ability to move faster after consolidating her clones into one person again; if she didn't run faster than me, the little boost she got there would keep her far enough ahead.



There was the family holding them back, yes, but there was also the possibility that there was a vehicle they could all climb into.  I could maybe keep up while riding Atlas, but I wouldn't be able to mount a serious attack while doing so.



I suspected the makeshift bug-barriers wouldn't hold up.  They wouldn't stand up to Triumph's shouts, and Ursa Aurora could summon her `bears'.  That was if they didn't choose to just charge through.



I needed more redundancies.  More fallback plans.  I began drawing out lines of silk at the lower half of the doorframes, while gathering the bulk of my bugs in the upper halves.



The question was, would they go through the doors or would they settle for the windows?  Would human habit triumph over slightly more abstract thinking?



The heroine led the way, already under attack from hundreds of bugs.  She grabbed a coat from the nearby rack and draped it over herself for cover against the swarm as she threw herself headlong into it.



Her legs caught on the tripwire and she tumbled down the stairs.  I rebuilt the barrier of bugs behind her, condensing it to the point that they couldn't see through.



I directed fly-borne spiders to extend threads around the heroine's arms and legs, as well as her fingers.  After a moment's consideration, I started packing them in her pockets, sending bugs crawling beneath her clothes.



Right.  A gun at her ankle.  I set spiders to the task of binding that up too.



\emph{Maybe she's a PRT officer?}\emph{Gun, no apparent powers?}



None of the rest of the family seemed willing to try exiting by the same door after she'd disappeared into the cloud of bugs and promptly shrieked.  Okay.  That meant I'd separated the family from the woman.  Triumph would catch up to them in a moment, so I had to make the most of this advantage if I was going to slow them down further.



I began moving the bugs from the door towards the family, simultaneously bringing more bugs in behind them.



They quickly realized they were cornered and backed into the nearby closet, closing it behind them.  I could sense them throwing coats and boots down at the gap between the bottom end of the closet door and the ground, trying to block my bugs from getting in.



Not quite good enough to stop the bugs, but I could leave them where they were.



As I was arriving on the property, the heroine was partially disabled and Triumph was en route.  Genesis would be pulling herself back together in another body, I supposed, but that wasn't so reassuring – the heroine had made a call to the PRT and there would be reinforcements on the way.



Okay.  How was I supposed to do this?  I had to deal with Triumph, but he was shutting down my swarm.  I'd probably lose in a straight up fight as well.  Whatever damage my bugs were doing with bites and stings, it wasn't enough to bring him down.  He'd kicked a long oak table that had to weigh six hundred pounds at a bare minimum, sent it skidding across the room.  There was no doubt he had some superhuman physique.  That same advantage might be giving him the ability to hold out against what my bugs were doing.



I was forced to scale up, to start injecting more than the trace amounts of venom, and I was all too aware of how easy it was to go too far or go over the top.



Life would be so much easier if I didn't give a damn about other people's well-being.



But I wouldn't be able to step up my attack without getting more bugs on him, and I wouldn't be able to do that without a different tactic.  I began pulling my bugs out of the house and gathering them.  By the time Triumph found his way to the hallway where his family was hiding in the closet, the bugs were almost entirely gone.



There were too few bugs there for me to catch it, but someone in the closet must have made a noise, because Triumph made a beeline right for them.  He stopped when he saw the heroine outside the door, lying on the ground under a carpet of bugs.



He said something to his family that was probably along the lines of `stay there' and headed for the door.  He could see the human shaped figures I'd molded out of bugs and positioned around the lawn and proceeded to gun them down one by one.  His shouts were short, on target and devastatingly effective.



The heroine was starting to get free.  Two additional versions of herself had appeared next to her, quickly searching out and cutting the silk cords that bound her.  At least I knew who I was up against, now.



\emph{Damn it}.  Unlike Oni Lee, Prism didn't materialize her duplicates along with whatever additional baggage her original self had.  None of the restraints and none of the bugs hampered her copies.  Not to mention that her guns were probably free as well.  I quickly directed Atlas to the roof and took cover in case she spotted me and decided to open fire.



``Sam!'' Triumph shouted.



One of the duplicates turned to look at him, her eyes widening.  She shouted, ``Careful!  Tripwire!''



He jumped at the last second, hopping over the tripwire.



\emph{Perfect.}



He landed on the stairs and stumbled.  The entirety of his focus was on the tripwire, on the stairs beneath his feet and on his attempt to keep from falling down the stairs with his unconscious burden.  During the Slaughterhouse Nine fiasco, it had come up that our species was pretty bad at looking \emph{up}.



I'd pulled bugs out of the hallway and from around the backyard and gathered them above the door, with airborne bugs helping by ferrying the slower moving ones up to a higher vantage point.  I gave the command at the same time that Prism shouted her warning, and the bugs dropped down onto Triumph's head.



Bugs tended to be very durable when it came to falling from high places.  It had something to do with the amount of air resistance when compared to their surface area or mass.  Something like that.  Either way, it barely did any damage to my swarm when they fell to the ground.



For Triumph, on the other hand, he was dealing with the sudden appearance of enough bugs that I could have formed three or four densely-packed swarm clones from their number, on top of the fact that he was carrying Trickster, who had to weigh one hundred and thirty or one hundred and forty pounds.  It probably didn't help that he was standing on a staircase and was already somewhat off-balance.



The timing proved to be lucky for me.  As strong as Triumph was, a strike at the right moment could still knock him off-balance.  I'd seen Alexandria do something like that to Leviathan, knocking something as big and horribly strong as the Endbringer to the ground.



Blind and struck at an opportune moment, Triumph fell.  I swept the bugs over him.  There was no room for holding back or playing nice.  I sent bugs into his nose and mouth, into his ear canals and biting at folds and crevices below the belt.



I could have been squeamish about that, but that would require thinking in too much depth about what I was doing.



I attacked his more sensitive areas, including the insides of his mouth, the sensitive edges of his nostrils and the insides of his ears.  Others stung and bit at his eyelids.  Some of my capsaicin-laced bugs flew from my cover at the roof's edge to Triumph and Prism.  I directed them to the vulnerable mucus membranes of the eye, the nose, the mouth – and again, beneath the belt – the urinary tract and anus.



The most important thing was to keep him from getting his bearings and dealing with the bugs.  I wasn't sure I'd be able to catch him by surprise a second time.



There was a secondary goal, too.  We'd come here for a reason.  If it came down to it, the mayor might change his tune once he'd seen his superhero son brought low.  This was leverage.



Prism was back on her feet, alongside her two copies.  I was forced to split my bugs among them.  What rules did she follow in terms of consolidating?  How did she pull back together, and what happened to injuries?  I knew she could survive if one copy was taken out of action.  If she had a knife wound on one body of the three she had active, did it stay? Or did the damage get divided to only a third of what it should be?



Whatever abuse my swarm was inflicting on her, she wasn't activating or deactivating her power like I might if I had her abilities at my disposal.  In her shoes I'd be splitting, spreading out, then consolidating into the body furthest from the bulk of the swarm.  My secondary goals would be getting to a vantage point where I could shoot down my assailant.  If I assumed she'd use the same basic tactic against me\ldots



I began gathering bugs around myself for additional cover and for a potential counterattack.



I swept some bugs over the surrounding landscape while I waited for her to either decide on a plan of attack or succumb to the bugs.  No threat of imminent attack by Coil.



It was spooky, having that hanging over my head.  I almost wished he'd attack already and get it over with.



I couldn't be sure how she spotted me, but Prism turned my way.  Maybe it was the size of the cloud of bugs I had around me.  It was almost a \emph{good} thing that I had her attention.  I had to take her out of action as soon as superhumanly possible if I wanted to get Trickster out of here before the reinforcements arrived.



She backed up, spreading out across the lawn.  One copy swatted at the bugs that crawled on her, another was gagging and coughing from the capsaicin, but they seemed to be holding out remarkably well.



One by one, they started towards me, running across the lawn.  I did what I could to obstruct and hamper them, but the rightmost copy slipped past the line of my bugs and bent down, the other copies snapping back into her body.  She flashed with light as she leaped with incredible strength.  She arced through the air until she was higher than the rooftop, set to land in front of me.



I sent the swarm forward to meet her, lines of silk stretched between them.  If I could disrupt her landing or even push her back enough that she missed the roof-



She split into three copies in mid-air.  The swarm caught the central one and tangled it.  It landed hard on the roof and rolled, falling a solid twenty feet to the ground, while the other two landed and skidded for a grip on the shallow slope of the building.  An instant later, she split off a replacement third, surrounding me.



Okay.  This wasn't as bad as it looked.  I had Atlas.  Yes, she could shoot him -and me- out of the air, but I had an escape route and this terrain suited me fairly well.  The shingled roof had a shallow slope leading to gargoyles and gutters at the edges, but I stood at the roof's peak, giving me the steadiest footing.



She was pacing, each of her copies slowly moving clockwise around me as they searched for a glimpse of me or some weakness.  I was doing much the same, trying to think of an approach that would work here.



What did I know about her?  Prism was one of Legend's people, which meant it was very likely she was being groomed to manage her own team somewhere.  Or she was considered effective enough to warrant fighting at Legend's side.  She would be \emph{good,} if nothing else.\emph{  }In a way, that was useful to me.  Any points where I'd had the advantage would be pretty indicative of her limits and weaknesses, since I wouldn't necessarily have to account for mistakes, accidents and idiocy on her part.



She hadn't immediately opened with her duplicates.  \emph{Why}?  Did she have a reserve of power she drew on?  Some restriction on when or where she could duplicate herself?



I'd seen her fight alongside Battery when they'd been tackling Mannequin.  They'd paced the fight so each of them took turns.  It made me think that maybe she needed to charge before she made her duplicates.  It would explain why she hadn't made them the second I'd outed them as superheroes.  That, or she'd had another reason and she needed time to \emph{recharge} after using her power.



One of her copies rubbed at her eye, then disappeared.  She replaced it with a version of herself that wasn't suffering.  \emph{That's one question answered, sort of}.



It was all too easy to see how she'd gotten this far.  I couldn't keep all three versions of her in sight at the same time and taking her out of action necessitated taking \emph{all three} versions of her down before her power recharged.  Couple that with how hard and fast she could hit?  She could be a nightmare.



\emph{Could }be a nightmare.  Emphasis on the \emph{could}.  I countered her powers, in large part.  If my suspicions were right, I had some kind of enhanced multitasking as a side-benefit of my powers.  I wasn't limited to seeing with just my eyes, so her circling me wasn't such a drawback, either.  And I could easily attack all three at once.



The trick would be doing it without giving her an avenue for attack.  She seemed reluctant to charge blindly into the swarm, but I was equally reluctant to use those same bugs to attack when I needed them for cover.  If I waited, her reinforcements would arrive, which put the pressure on \emph{me} to end this.



I let out one deep breath, then carried out my plan of attack.  I unwound the silk cords I'd gathered and climbed off Atlas, sending him out with one, taking hold of another.  Crouching to make myself a smaller target, I sent my bugs out to carry the string.



She moved to try to find a point where the swarm was thinner, while avoiding the clusters of bugs.  It wasn't quite fast enough.



I'd used my silk to grab Triumph's cell phone and yank it from his hand.  I did much the same thing here.  One silk cord wound around the throat of Prism A, masked by the presence of bugs.  Another wound around the leg of Prism B.



In the same moment I pulled on the cord leading to Prism B's leg, Atlas pulled back on the cord leading to Prism A's throat and my swarm bull-rushed Prism C, aiming to drive her off the roof through sheer force of numbers, surprise and the pull of silk cords.



A and B fell from the roof, then promptly disappeared, consolidating into C.  She flashed with a light I could see through the dense cloud of my swarm and charged forward.  In a heartbeat, she was out of my swarm and capable of seeing me.



Prism reached down to her ankle and grabbed for her gun.  It didn't come free of the holster.



She could come with baggage she wasn't aware of?  She had \emph{some} control.  Maybe she had to go out of her way to exclude certain matter or material from her duplicates?



She formed two new duplicates, and I caught a glimpse of them pulling their guns free before I was back in the cover of my swarm.



At my bidding, Atlas flew low, close to the building where he was out of sight of the rooftop.  He circled around until he was behind me.



I formed a crude swarm-clone and then stepped back onto Atlas.  I didn't sit, but relied instead on control of his flight and the angles he moved to help match my own balance.  We swiftly descended to the ground as the part of my swarm that wasn't dedicated to forming my double moved forward to attack once more.  I could hear and feel Prism firing blind into the center mass of the swarm.  She was mad now.  I'd nearly taken her out.



Had to think ahead.  She would use the same tactic as before, consolidating to barrel through, she'd see my decoy and attack it, then come looking for me.



I reused the cord that I'd had around her foot, winding it around one gargoyle.  The trick was figuring out which copy I'd target.  This wouldn't work if she unmade the copy to supercharge one of the other ones.



I'd have to bait her.



My bugs tied the silk around one of her wrists, letting the rest sit slack against the rooftop.



As I'd expected, the three of her appeared at the edge of the roof, looking down to the ground to find me.  I was already heading for Triumph, putting myself roughly between them and him.  It would serve two purposes, the primary purpose being that it would give them reason to think twice before shooting.



They leaped, then consolidated with a flash of light before they hit ground, to absorb the impact with superior strength and durability.



Only the silk thread connected the gargoyle to the Prism-duplicate closest to me.  She didn't make it all the way to the ground.  In the blink of an eye, she was whipped sideways, one arm hyperextended.  She dangled for a second or two before the silk gave way and she fell to the ground.



The power boost was temporary enough that she wasn't invincible as she made her awkward landing.



I hurried to where Triumph and Trickster were.



Triumph had managed to move a short distance away before collapsing again, and remained buried beneath a pile of my bugs.  He wasn't doing well.  It was very much what I'd been concerned about at the outset, going a little too far.  On their own, the choking bugs, the inflammation from the capsaicin and the stings weren't too bad, but together?



I eased up on him just a bit.



A quick survey of the area told me that there weren't any imminent threats in the vicinity.  Prism wasn't standing back up.  There was a kernel of something where Genesis was rebuilding a body.  The policeman Trickster had swapped with was making his way back here, and other cops were en route as well.  I still had a minute or two.  The mayor, I noted, had left the closet, heading for a room lined with bookcases and cabinets.



My swarm sense allowed me to feel him opening one cabinet, unlocking and opening a drawer beneath.  He retrieved a shotgun from the cabinet above and a box of ammunition from the drawer.



I could have taken him out right there, hit him hard with my bugs.  I didn't.  I'd have to leave after that, and I could almost believe that he'd be angry, that he'd argue for the city to be condemned with even \emph{more} fervor than he might have otherwise.  This could backfire if we simply left him wounded.



Instead, I focused on building up several swarm-decoys before he could make his way to the back door.  I lifted Trickster up and draped him across Atlas' back, binding him in place with silk thread.



The mayor had loaded the gun by the time he was in the doorframe.  He must have overheard Prism shouting about the tripwire, because he moved fairly gingerly through the threshold.  His eyes roved over my massed decoys, his gun drifting from side to side as if he was getting ready to shoot at any instant.



``Mayor,'' I spoke to him through one decoy, buzzing and droning the words.



He turned and fired, blowing a hole through its chest.



``Your son is-'' another spoke, while the first reformed.



He fired again, blasting the head off the second decoy.



``-Dying'' the first finished.



He was in the midst of reloading the shotgun when he stopped.  ``What?''



``Suffocating,'' I spoke through a third decoy.



``No.  He-''



``Stings aren't helping,'' I began rotating through the decoys, each speaking a different sentence.  ``The allergic reaction's causing his throat to close up.  He can't swallow.  There are bugs in his mouth, nose and throat.  They're making a dangerous situation worse.  He can barely even cough to clear his airways to breathe.''



``If I shoot you-'' he tightened his grip on his gun.



``My power rewrites the basic behavior patterns of my insects from moment to moment.  If you shoot me, they'll continue attacking, and there'll be no chance of getting them to stop.  You'll be sealing Triumph's fate.  \emph{Rory's }fate.''



``He's stronger than that,'' the mayor said.  He didn't sound sure.



``We all need to breathe,'' I replied.  I could have said more, but I judged it more effective to let the thought sit with the mayor.



I cleared the bugs away from Triumph, giving the mayor a visual of his superhero son lying on the ground, struggling.  To make his struggles a little more pronounced, I briefly increased the pressure, shifting the bugs to limit the available oxygen.  I wasn't sure exactly how much danger he was in, but he wasn't doing well.  As much as I wanted to pressure the mayor, I was ready to apply the epipen the second Triumph's breathing slowed enough.



For long seconds, the only sounds were the small noises that Triumph could manage, gagging, feeble coughing and wheezing.



``You're going to kill him?''



``I would rather not.''



``He's my boy,'' the mayor said, his voice suddenly choked with emotion.



``Yeah.''  I blinked hard, to clear my own eyes of moisture.  I couldn't meet his eyes.  I focused my attention on Triumph instead.



``I only ever wanted what was best for him.  I didn't want this.  Please.''



I couldn't muster a response.



``Please.''



This time, I thought maybe I \emph{could} have said something to him.  I deliberately chose to remain silent.



``Hey!'' he roared.  He raised his gun, cocking it, ``Don't ignore me!''



Triumph coughed, then his chest heaved.  I forced a bug down his throat to check and found it almost entirely closed up.  I moved the bug away so it wouldn't block the already limited airway.



``He's almost stopped breathing,'' I said, almost in shock at what this had come to.  I'd been so preoccupied with Prism, I'd pushed things just a bit too far, I'd allowed my bugs to sting him because he was tough enough to take it, but I'd forgotten to account for the other variables, the pepper spray and the reduced air volume thanks to the bugs in his nose and mouth\ldots



I looked at the mayor and found his gun pointing at me.  \emph{I spoke with my own voice.}



With a calmness that caught \emph{me} off guard, I said, ``It's not too late.''



The voice of the sixty-ish man who could address whole crowds with conviction and charisma sounded painfully feeble as he spoke, ``CPR?''



``Yes.  But primarily this.''  I drew an EpiPen from my utility compartment and held it up.  ``Do you know how to use it?''



He shook his head.



``I do,'' I told the mayor.



Even as I was painfully aware of Triumph's slowing struggles, his body swiftly growing weak in the absence of air, I waited.



``Use it!''



Again, I didn't move, I didn't respond.  I saw Triumph's hand close into a fist and then stop.



\emph{A person can hold their breath for roughly two minutes\ldots he's still almost breathing, but how much breath is actually getting in and out of his lungs?}



``Use it!'' the mayor threatened me with a motion of the gun.



``We both know you can't use that.  I'm the only one who can save Rory.''



He sounded more like he was trying to convince himself than me, ``There'll be instructions.  There'll-''



``And if I break the needle in my death throes?  Or if I drop it and you can't find it in time to read the instructions and deliver it?  Or if a stray shell fragment hits the needle?''



The mayor's voice was a roar.  It was as if he could will me to act by sheer emotion and volume.  ``He's not moving!  He's \emph{dying}!''



``I know.''



Seconds passed.



\emph{How long can I wait until I break?}



The gun clattered to the grass, the mayor dropping to his knees.  His voice was hollow.  ``I'll give you what you want.  Anything.''



I didn't waste a second in stepping to Triumph's side.  I tilted his head to establish the airway, swept my fingers and bugs through to clear away the worst of the blockages and mucus and then pulled his pants down.  I stabbed him in the thigh with the pen.



I couldn't afford to stay.  I couldn't be the one to administer the ongoing care Triumph needed.  Coil was still after me, the reinforcements were coming, and I wasn't sure I could bring myself to leave if I stayed much longer.



``Do you know how to give CPR?'' I asked.



``No.  But my wife-''



``Bring her here.  \emph{Hurry}.''



He practically crawled on all fours in his hurry to get up the stairs and up to where his wife waited in the closet.



``Sorry,'' I murmured to Triumph.  ``I didn't want this to go this far.''



He wheezed, a strangled squeal.



``Yeah,'' I told him.  ``I know.''



The older woman bent over her son and began administering CPR.  I watched a few seconds to ensure she was doing everything right.  I threw a second EpiPen to the mayor.  ``In fifteen minutes, if the paramedics aren't here yet, use that.''



His hands were shaking so violently I was momentarily worried he'd break it.



``Washington,'' I told him.  ``The city survives.''



He nodded.  There were tears in his eyes, this stubborn man who'd talked so casually with the supervillains who had invaded his home and threatened his family, who'd tried to take me on with a shotgun.



I turned to walk away, my swarm-decoys moving in the same direction.  Before he could think to go back for the shotgun and shoot me in the back, I had a swarm gathered around me, hiding me from view.





