





I passed the invisible boundary between the neatly manicured lawn of the mayor's expansive backyard to the tall grass at the glade's edge.  My hands were shaking and my breathing was heavy.  I hadn't done anything more strenuous in the past few minutes than talking to the mayor and walking at a good pace, but my body was reacting like I'd just sprinted halfway across the mayor's property.



I put a hand on a tree as I walked, as if it could steady me and keep me from falling.  I wasn't in any danger of falling that I was aware of, but it was reassuring nonetheless.



Damn him.  How big was his property?  And he could still afford to hire someone to cut his grass?  Eat a nice dinner on a huge wooden table, complete with courses?  Blithely ignoring what was going on in the rest of the city with his superhero son and superheroine date?



No, try as I might, I couldn't bring myself to get angry.  Couldn't blame \emph{him} for what I'd done.



I'd deliberately let someone come within seconds of dying, and he hadn't been a monster, like Lung or the Slaughterhouse Nine.  He hadn't even necessarily been a \emph{bad person}.  If I'd waited just ten or twenty seconds longer, he might have stopped breathing.  CPR would be that much more difficult with a closed airway, and he could have died or suffered brain damage while they attempted to revive him.



Of course, my first aid knowledge wasn't all that recent or complete.



I let go of the tree, adjusted my sling and moved on.  Drawing my cell phone from the armor at my back, I made a call.  ``Cranston?''



``What can I do for you, Skitter?''



My voice sounded too calm for how my body seemed to be reacting.  ``Need an ambulance to the mayor's residence, backyard.  There's a young man having breathing difficulties.  Can you use untraceable channels to get in touch with emergency services?''



``I'll do that.  Anything else?''



``Tell Coil the job's done.''



``The second this phone call is over.''



I hung up.



Triumph's family would probably do that anyways, but it made me feel a little better.



I couldn't afford to dwell.  I headed for Genesis, stalling her movements by signaling her with my bugs.  I wrote out a message: `Job done.  Trickster hurt.  Need help taking him to Coil.'



I directed her to me with my bugs, drawing arrows in the air.  A minute or two passed before she caught up.



Genesis had decided on a form that was an overlarge woman's face carved out of bone, surrounded by long, thin, branching tentacles.  She would have come up with that as a counter for Triumph and either Prism or Ursa Aurora; something that could take a heavy hit, either from a bear made of forcefields or Triumph's shouts and punches.  It would also be pretty effective against Prism for the same reasons I was: Multitasking and the ability to handle multiple foes at once.



``Where's Trickster?'' she asked.



I brought him down from above the treeline, unconscious and strapped to Atlas' back.  ``I can't carry him all the way back.  It's too far, and it'll be too slow.  Atlas is leashed to me by my maximum range.''



\emph{And as long as I'm on foot, I'm vulnerable to any attacks from Coil or Prism's reinforcements}.



``You want me to carry you?''



I shook my head.  ``I want you to carry \emph{him}.  Flying Atlas is hard enough as it is without an uneven weight on top of him, and if Trickster wakes up and starts moving, he's going to fall.''



``Fine.  \emph{Damn it}.  Making a new body's slow when I'm this far from myself.''



``Can you make it at the far end of this glade?  I can jog there by the time you're done, and I'll bring Trickster.''



She didn't respond.  Instead, she began breaking down into a gelatinous, blurry mess.  Her power was like mine, I supposed.  It took time to prepare.  I had to get my bugs to the battlefield, she had to put herself together.



I checked Trickster was securely in place, adjusted my sling so my arm wouldn't bounce too much and then hurried for the meeting place.  Atlas followed, flying just above the treeline.



It was times like this that I felt less normal, less human.  It was dark, the foliage overhead dense, branches blocked my way and the ground was riddled with roots, stones and uneven footing.  It barely mattered.  My bugs flowed ahead of me to check surfaces, clinging to branches and carpeting the ground.  I passed through the trees as though I'd spent my life among them, memorizing where everything was.  I extended my foot just a bit further to accommodate the slope ahead of me, ducked a branch with wickedly pointed tips and found a handhold on another branch to help myself hop over a spot where water had pooled.



I liked running.  For months, I'd used running as a way to forget about whatever was plaguing me.  Before, it had been the bullying.  Then it had been the pressures of dealing with the Undersiders, my undercover ruse.  Separating from my dad.  Dinah.  The fallout from the Endbringer attack.  Coil.



The times I hadn't run, I'd felt like I was losing my mind.  Did correlation equal causation, there?  Or was it just that the moments I was unable to run were the same moments I was  under the most stress?  When the Slaughterhouse Nine had been in town, when I'd been living in the shelters after Leviathan hit the city, before I rejoined the Undersiders?



Either way, it was good to break free of my thoughts on Triumph and what I'd done to him. I could focus on breathing, on putting each foot exactly where it needed to be, keeping my balance and letting my subconscious guide me through the woods.



I felt vaguely disappointed when I reached the point where the small forest ended and the roads began.  One of the busiest streets in Brockton Bay was desolate, a lone car cutting a path through the shallow water as it headed away from the city.  I stayed in the shadow of the trees until it was well out of sight.  I didn't want to do this, didn't want to step back into the city and face everything that waited for me there.  The threats on my life from an employer who divided and pruned realities was only a small part of that.



I would have left, if I could afford to.  If Dinah and my people could afford for me to.



My bugs found Genesis, and even with the indirect route I'd taken, I reached her before she was fully formed.  She looked like a bison with wings, but her back had a bowl-shaped depression, and she had stubby little legs and antennae.  Since she didn't have the means, I was left to try to ease Trickster into the basin.  I could see why she did it, cradling him and ensuring he couldn't fall, but it was still dangerous and tricky to move him with just the one arm.  I wondered if she'd seen the sling.



We took off, and Atlas proved faster than she was.  She had to ride the air currents and she was heavier overall.  I scouted forward some in case we crossed paths with Legend or any other heroes.



I paused on one rooftop while I waited for her to catch up again.  I drew my cell phone and called Tattletale this time.



``Skitter?'' She answered on the first ring.



``Job's done.  Already told Coil.  Triumph was there, along with Prism.  They hurt Trickster, took Genesis out of action.  I stopped them and finished the job, got the mayor to agree to the terms we wanted.''



``Are you still there?  At the mayor's place?''



``No.  Just left.''



There was a pause.



``That doesn't make sense,'' she told me.



``What doesn't?''



``We're clear to talk, no bugs, I'm ninety-nine percent sure.  So listen, if Coil wanted to assassinate you, that'd be his chance.  Once you leave the mayor's property, that's it.  He doesn't know where you're going.''



``Trickster got hurt,'' I told her.  ``Maybe he was supposed to do it?''



``Maybe,'' she admitted, ``But that still feels wrong.  Why wouldn't Coil have a backup plan?''



``Or maybe Dinah's power is working, and he's got some bigger plan in mind?''



``I'm at his base right now.  It doesn't fit with his movements.  He's not really visiting her.''



I shivered.  Visiting her, dosing her with drugs, interrogating her for answers about his grand plan\ldots I hated the images that popped into my mind when I thought about Dinah in captivity.



``Listen,'' she said, ``I'm going to try to find out more.  I'll call you back.''



``I don't like that you're there without backup.  You said he might want to get rid of you too.''



``I'll know if he does.''



``Like you \emph{knew} he'd try to kill me?''



Another pause.



``I'll call you later,'' she said.



The line went dead.



I reluctantly put my phone away.  I had a hollow feeling in the center of my chest.  A huge part of me wanted to call Grue, but I couldn't convince myself that it was really what I was \emph{aching} for.  I might have anyways, but I wasn't sure what I would have said.  Would I have asked for a hug, another cuddle?  For advice, tactical suggestions?  For reassurances?



I wouldn't have said the thought had ever explicitly crossed my mind, but somehow I'd always assumed that I'd know what to do when I got into a relationship.  I didn't want this thing to be designated the nice memory that we avoided mentioning until things had returned to the old status quo.



But I wasn't sure he was the person I wanted to reach out to.  The people in my territory?  Was I seeking some validation there, some cheers, smiles, hugs and other assurances that I was really on the right track, doing the right things?



I couldn't be sure.



I met with Genesis in the air, flying just beneath her so our heads were as close to one another as possible.  ``Is he okay?''



``He was awake a second, then went under again,'' she said, ``Might be a good thing.  He's hurting.''



``Probably.  Why?  Why did he pick a fight like that?''



``It's how he operates.  I'm not saying this is usual, or that this wasn't an extreme case, but\ldots it's always how he dealt with things, big or small.  The worse things get, the more stubborn and cocky he gets in going up against them.  It worked when we were just messing around together, just playing around.  But we were never suited to be\ldots I dunno, a family?''



``A family?''



``We've spent two years together, with just each other.  I don't know what you could call us, if not that.''



``Why don't you quit?  Split up?  Is it Noelle?''



``She's only half of it,'' Genesis said.  She didn't volunteer anything more.



We flew in silence for a few long seconds.



``Don't blame him, okay?  He has his way of handling stuff, but those methods don't scale up so well when we're dealing with stuff this screwed up.''



``Things are getting better.  The Nine are gone, we're cleaning up the city, our enemies are getting driven out of Brockton Bay.''



``Better for you, maybe, but those are your priorities.''



I didn't respond, wasn't sure how to.



``Just\ldots don't blame him.  I'm sorry things got so bad tonight.''



``Okay,'' I said.  I hadn't meant to get caught up in a conversation.  I saw a chance to say what I wanted to, ``Are you good with going to Coil's on your own?''



She looked surprised.



It was too dangerous to meet with Coil right now.  I wasn't thinking straight, and I wasn't willing to walk into the lion's den.  Another day, under different circumstances, with backup?  Maybe.  But not now.



``I'm going to head back to my territory,'' I lied.



``Yeah.  Sure.''



``Okay.  Good luck?  Coil can call me if he needs anything.''



``Alright.''



I veered off to head north, leaving Genesis to continue in the direction of Coil's headquarters.



As Tattletale had suggested, the window of opportunity had passed.  If I returned to my territory, would I be walking into a trap?  The same could be true if I went to any familiar place.  Coil had enough soldiers to have one lying in wait in any given area.



On the other hand, if I broke pattern and stayed somewhere off his radar, I'd be letting him know I was suspicious.  That might be all he needed to decide to step up his plans and go all-out.



I came to a decision, all my disparate thoughts and concerns snapping together into one simple, inelegant solution.



Too dangerous to go to my territory.  I set Atlas down on top of the tallest building in the area, climbed off and sent my bugs into my territory instead.  They flowed into my lair as a mass.  I left some in the appropriate terrariums to restock my supply of some of the rarer spiders and larger beetles.  The rest passed through the upper floors of my lair and retrieved the necessities.  They returned, surrounding Atlas as a cloud.



Once Atlas had landed beside me, I began getting everything in order.  Atlas held my rain boots in his front claws and carried my backpack and some of the clothes I'd had him pack on his back.  Using my hand, I swatted other items through the backpack's opening as my bugs brought them into position – underwear, socks, wallet.



I ran one hand over Atlas' rough exterior.  ``What am I going to do with you?''



Atlas didn't have the instincts to operate on his own.  He was an entirely unique creation, designed from scratch with no real blueprint or model for behavior.  He couldn't move, couldn't eat and couldn't defend himself if I wasn't in range to control him.



I'd have to figure something out.  Some place I could stick him so I could keep him close.



I picked out what I wanted to wear, checked there wasn't anyone nearby and changed on the rooftop.  I had to take off the sling to free my arm, which maybe wasn't the best idea, but I was gentle with my shoulder as I worked my way into a tank top.



When I was changed, I fixed my sling, I packed my stuff in my bag and bound my costume loosely in silk to keep it compact and tied that package loosely to Atlas' back.  I wouldn't be going anywhere without him, and wherever I was, he could probably bring my costume to me faster than I could access whatever hiding place I'd chosen.



I double-checked there wasn't anyone watching, stepped up onto Atlas' back and stayed standing as he lowered us to the street.  I skipped down with a bit of a splash, slung the backpack over my good shoulder and started walking.



Things were getting better.  The flooding was more under control, and less streets were sitting beneath inches of water.  The work my people had done in our district had helped, here.  We were downhill, and the efforts in clearing out the storm drains and dismantling the trash and rubble that was trapping water in certain areas had freed the water to flow down towards the beaches.



Still, that wasn't saying a whole lot.  There were too many areas where it was dangerous to walk without proper boots, due to the glass and the wooden boards with nails in them. Piles of trash sat everywhere, with nobody to clear them away.  When people had run out of plastic bags, they began throwing the trash in cardboard boxes or plastic totes.  When \emph{those} had proved too short in supply, they'd started throwing debris and litter wherever they pleased; out windows and into alleyways.  I could see rats in the spaces between some houses, not even shy about being out in plain view while I walked by with my oversized rain boots.



Plant life was alternately dying and flourishing, with trees and lawns drowned and algae and moss blooming.  Weeds were cautiously emerging wherever there was ground to take root.



It was funny how nature reclaimed this world in its own way.  It was silly to say humans were destroying the environment; we were simply changing it.  Nature would persevere until the world was a barren wasteland.  Whatever apocalypse Jack was supposed to set in motion, I suspected Jack was right in what he'd said to Bonesaw.  Something would undoubtedly survive, and this sort of thing would likely happen across the world, starting in the cracks, spreading out, only to overwhelm and bury the ruins of civilization.



A weird direction for my train of thought, but this was one circumstance where I didn't want to think too much on things beforehand.



I stopped, not out of hesitation, but nostalgia.  The wooden staircase in front of me had rotted out on the bottom-most step.  Not recent, not a fault of Leviathan or the city's conditions.  Older.  I skipped past it and headed up to the front door and rang the bell.



My heart pounded.  I tried not to think about anything particular.  Didn't want to chicken out.



The door opened, and I found myself face to face with my dad.



It took all the courage I had not to turn around and run.  I was such a coward.  I'd been like this with school; I'd stopped going to classes for reasons that were more or less reasonable in the moments I'd made the decision, and somewhere along the line, I'd continued to avoid school because I didn't have the courage to own up to my previous absences.



Only this wasn't school.  It was my dad.  He still had marks all over his body where the glass had cut him, dried scabs in lines and circles all over his face and arms.  He had one large bandage on his shoulder.  Shouldn't he have healed by now?  Or had it been that bad?



``It's good to see you,'' he said.  His forehead was creased in concern.  ``You're hurt.''



I looked down at the sling.  ``It's not major.''



``Is it why you-'' he said, stopping himself as if he didn't want to jinx things and scare me off with a poor choice of words.



``No,'' I said.  I found myself searching for an explanation, opening my mouth to respond and then closing it when that explanation didn't readily come.



\emph{He's my boy}, I could imagine the mayor's voice, the pain and raw emotion I'd heard.  \emph{I only ever wanted what was best for him}.



I just had to look my dad in the eyes, and I could see that same expression in my dad's eyes.



``No,'' I said, again.  ``I just saw someone nearly lose her daughter.  It made me think of you and mom.''  I'd changed the genders on the spur of the moment to be safe.



As if I'd prodded a wound, I could feel that deep-seated ache from earlier come alive.  I wanted to look away, but I forced myself to meet my dad's eyes.



``Do you,'' he said, pausing, ``Want to come in?''



I nodded.  He stepped out of the doorway and I stepped into the house for the first time since Shatterbird had attacked.  That had been the start of June, or thereabouts.  I hadn't exactly had time to look around, nor had I really been in a stable state of mind.  The last time I'd really been able to look around the house had been the start of \emph{May}.  Nearly two months ago.



I looked at the mantlepiece above the fireplace.  Things had been rearranged.  There was a small clock with a broken face, a family picture of Dad, Mom and me that had survived Shatterbird's attack and a little statue/candlestick featuring a woman with a flowing dress.



I touched the statuette.  There were memories there.  Too many things in the house had them.  The statuette was part of a pair.  My mom had bought them at the market.  The overly tall, skinny, exaggerated figures had seemed to match my mom and dad, in a way.



``Where's the husband statue?  Were you robbed?''



I looked at him, and he looked embarrassed.  ``I traded it away.  More than a few things.''



``Why?  For what?''



``Selling and bartering for food,'' he answered.



``But there's supplies.  Did you not get enough, or\ldots'' I trailed off.  Why was I attacking him? Accusing him?  Was it guilt, failing to look after my dad and make sure \emph{he} got the supplies he needed?



``The explosion with the glass.  I suffered some minor kidney damage.  The doctor advised me to up my iron and protein intake while we wait to see if it'll scar.  Not nutrients you find in good supply in supply kits.''



\emph{Kidney damage}.



``Is that the worst injury?  You're otherwise okay?''



``I'm mostly okay.  Better than most, thanks to the warning you gave me about the Slaughterhouse Nine being in town.  Some of my coworkers owe you thanks as well.''



I nodded.  I was glad people were okay, but the fact that word was spreading, it put me in a dangerous spot.



``But I should be the one asking how \emph{you're} doing.  What happened to your arm?''



``Foreign body got trapped in there at some point,'' I said, ``Needed minor surgery.''



I could see the alarm crossing over his face.  Had he heard something?  Flechette passing on a message that people with injured shoulders-



``\emph{Surgery}?'' he asked.



``It was only local anesthetic.  Really.  Not that big a deal.''



I looked over the bookshelves.  One of the better pictures of mom and me had been destroyed by the explosion of glass, ripped to shreds.  He had to have picked up that frame and stood it up on its own, sometime after Shatterbird's attack.  I prodded at the picture, as if I could push the tattered remains back together.



``You're so different,'' he said.  ``You're standing straighter, dressing like you aren't trying to hide in your clothes, moving with more purpose.  I think you've grown, too.  So many people, they seem like they've been burdened by what's going on, they've given up a little, lost important things.  That just makes the contrast between you and them that much stronger.''



I turned around.  Was I?  ``I don't feel that much stronger.''



``I spent fifteen years raising you.  Two and a half of those years I spent raising you alone.  I can see a difference.''



``I'm not saying there isn't a change.  There probably is.  I just- I dunno if I'm better because of it.''



``Oh.''



A silence stretched out.  Neither of us were adept conversationalists, and any familiarity we'd had was gone.



``Do you want to sit?'' he asked.



I nodded and seated myself.  There were papers on the coffee table.  Two loose stacks, headed with the title `Know where you are'.  They looked as though they had been printed using a fifteen year old photocopier.  I picked one up.



`Know where you are:



The area extending east of Captain's hill is believed to be under claim by the supervillains Grue and Imp.  Both are members of a group known as the Undersiders, who have joined with the Travelers in an unnamed alliance.  These villains will \underline{not} attack civilians unless provoked, and clean-up is tentatively progressing throughout the area with no objections from either villain.



Grue has the ability to create clouds of darkness.  Should you find yourself in one of these clouds, retreat to the nearest cover you remember seeing and assume there is immediate and present danger from vehicles, gunfire, moving pedestrians and fighting between capes\ldots'



I put it down.  There was more, noting a lack of information about Imp as well as the gangs and possible rivals that Grue and Imp might be fighting with, but it was over a week out of date.



The second paper:



`Know where you are:



The area extending west of the ferry station north, including the factories and the remains of the Boardwalk, is believed to be under claim by the supervillain Skitter.  Skitter is a member of the Undersiders, who are allied with the Travelers in an as-of-yet unnamed alliance.  Skitter is an unpredictable young woman tending towards acts of apparent kindness to those she deems her subjects and bursts of sudden and extreme violence towards those she sees as her enemies.  The city is not funding work in her territory, as Skitter is handling matters there.



Skitter controls insects and senses what they do.  Anyone with allergies to stings or insect bites would be advised to leave this area.  She offers food, shelter and care to anyone who agrees to work under her, but the Dockworkers Association cannot suggest that anyone accept her offers, as her ulterior motives are unknown.



This area is not currently the site of any ongoing disputes between capes.  There is limited power in this area.  There is limited cell service in this area.  There is not water service in this area.'



Again, a little out of date.  Our water was running.  Still, it was startling to see this here.  From the beginning, I'd wanted to keep that part of my life and this part of my life separate. It had been a fierce enough desire that I'd avoided taking revenge on the bullies because of it, at least a little, and it might have had something to do with my running away from home.



``Your DAU has been putting these up?''



``Yes.  Making sure people are informed.  Too many stories of people taking the wrong path through the city and getting cornered by a mutant dog the size of a small tank.''



``Right.''



``You said you were staying outside the city, with Lisa's family?  At the North end?  How did you get here?''



``I walked across the market, down to the Boardwalk and crossed through Skitter's territory.''



I was pretty sure I wasn't acting strange as I said the name.



``They didn't give you any trouble?''



``They stopped me at the border and I asked permission.  They were nice about it.''



``Okay.''



Lie after lie.



Another uncomfortable pause.



``Have you eaten?  I have some liver and mashed potato in the fridge.''



``I've eaten,'' I lied.  No use taking some of my dad's money when he was having to sell stuff to get food.



``Would you like some tea?''



``Please,'' I said, grateful for an offer I could accept in good conscience.  He retreated into the kitchen to put the kettle on.



I looked around.  It didn't feel like my house anymore.  I'd only been gone two months, but things were different.  Things in the house had moved, or been sold, or they'd been damaged by Shatterbird's attack.



The atmosphere was different too.  I wasn't sure how much of that was the humidity, the lack of upkeep and the fact that the family of two had been just a family of one for nearly two months and how much of it was me.  It was all too possible that I was viewing my surroundings in a different light, tinting things with my paranoia about my dad making the connection between me and Skitter, viewing things more negatively because of my guilt over leaving him.



My dad rejoined me.  ``If you give me a minute, I can make your bed-''



``I'm not staying,'' I blurted the words.



``Oh.''  I could see the pain on his face.



In the mutual awkwardness that followed, the vibration of my cell phone was a mercy.  I picked it up and checked the display.  Heart-c-c-apostrophe-square.  Tattletale.



``I'll be right back,'' I said, hopping off the couch and hurrying out the door as I hit the button to pick up.



\emph{Please be okay}, I thought, shutting the door behind me.



``Hey,'' she replied.



``You're okay?  Cactus-B.''



``Sun-Y.  Or Sun-N.  Whichever you prefer.''



``I'm not sure what color that's supposed to be.''



``Neither am I.  Um.  So I talked to Coil.  Things have been clarified some.''



``Okay.  Should we-''



``It's fine, pretty much, even if he's listening in.  You're not in danger.  No threat on your life at this present moment.''



``Okay,'' I said, not sure how to expand on that.  She hadn't precisely said it was Coil that was the threat, so maybe she was hedging her words to be safe.



``Which scares me,'' she confessed.



``Scares you?''



``Um,'' she said.  It wasn't like her to be lost for words.  ``I told Coil that Trickster got injured. I wasn't sure if you'd told him.  He didn't seem concerned.  There was zero indication that his plan had been disrupted.  Told him you were on your way back, again, no concern.  Everything that had been telling me he was harboring plans to assassinate you was telling me he wasn't and hadn't ever been, this time around.''



``Your power lied to you?''



``Um.  That's what I thought.  I was thinking maybe I was working under a mistaken impression, tried adding and removing the elements to see if I could get a different result, interpret his earlier behavior differently.  No go.  And I was doing all this while having a perfectly normal conversation with Coil, until he says something like `Very dangerous.  You want to be careful who you're picking a fight with.'''



I felt my blood run cold.  I had to sit down on the stair.  ``He meant-''



``Oh, he totally meant.  If I was one-hundred percent sure he was planning on killing you before, I'm five-hundred percent sure he was telling me he knows what we're up to.''



``What should I do?  What should \emph{we} do?''



``I don't know.  But that wasn't the end of it.  I was still processing what he'd just said when he stepped toward the door to leave.  He put one hand on my shoulder, leaned close, and he spoke in this very quiet voice.  He said, `Be \emph{careful}, Tattletale.  I value your service, but you should know your power isn't as reliable as you like to think.'''



Sounding civil and caring while expressing a very clear threat.  ``So the fact that it lied before-''



``It didn't lie, Skitter.  I said he was testing me, before.  He was, just not like I thought.  He's found a way to confuse my power, to counteract it.  This thing with the hit on your head.  It was just to scare us.  To let us know that any security my power afforded us, it doesn't apply to him.  He can make us think you're going to be killed when you aren't, and-''



``And the opposite is true.  He can make us think we're safe when we aren't,'' I finished.



``Exactly.''



``What do we do?''



``I don't know,'' she said, again.  ``Listen, I've got to call the others.  Are you with Grue?''



``No.  Maybe I'll head that way before the end of the night.''



``We'll figure something out,'' she said.



\emph{Figure something out?}  Coil was on to us, he'd effectively taken Tattletale out of the equation, and by all accounts, he seemed confident enough to continue letting us work for him, despite our intended mutiny.



I couldn't bring myself to agree.  ``Bye,'' I said.



``Bye.''



I hung up.



Before I could convince myself to head back to my territory and start plotting some counteroffensive, I stood from the stair and walked back inside.



Seeing my dad's face, I was reminded of the dream I'd had, where my dad had turned out to be Coil, where I'd taken too long and Dinah had died.  I looked away, made my way back to the couch.  My dad set a cup of tea down in front of me, then sat beside me.



I wasn't religious.  Didn't believe in a higher power.  Mundane government was crappy enough, the idea of a divine one simultaneously scared me and made me want to laugh.  As a consequence, when I thought of a soul, I was thinking more about some collection of the abstract parts of the mind that covered a person's mental and emotional well-being, their psyche and the defining aspects of their personality.  A more religious view of the soul would probably add up to a rough equivalent.



Whatever my overall motives might be, some part of what drove me was some desire to patch up the damage, fix that part of myself that had been taking a beating ever since I'd gotten that call about my mom's death.



Only it wasn't working.



Try to help the city, help the heroes, shore up my sense of self worth, find myself fumbling, tearing and discovering fresh holes in my subconscious makeup, with Dinah and my betrayal of the people who'd become my friends, betraying myself by failing to keep to that overall goal.  And there were other moments, moments where I'd been brutal and violent, accidental or otherwise.  Moments I'd made sacrifices, or where I'd been callous.  It wasn't subtle, either.  The stack of papers in front of me said it, clear as day.  \emph{Sudden and extreme violence.}



Even coming here, it had been at least partially motivated by my desire to fill that hole deep inside, that spot where family was supposed to fit.



I sipped on the tea.  My dad had made it with sugar, not honey.



This\ldots sitting here and drinking tea with my dad, my head someplace else entirely?  It wasn't fixing anything.  Wasn't mending or filling anything.



I sipped again, then drank it in big gulps.  It burned going down, and I pounded my collarbone, as if I could banish that sensation.



``Taylor?''



I stood and picked up my backpack and shrugged it over the one shoulder.  ``I've got to go.''



He stood too.



``I'm sorry.  We're- we're heading back, and it's dark, so we're going with a group.''



``I'll come.''



``No.  You'd be alone going back.  It's okay.''



He looked hurt.  ``A hug?''



I hesitated, then stepped close and hugged him with the one arm.  He gingerly wrapped his arms around my shoulders and squeezed.



``I'll be back,'' I mumbled into his shirt.



``No vague promises.  You're going to promise,'' he said.



``Day after tomorrow?''



``Okay.  I don't have work then, with the mayoral elections.  We can eat lunch here and then go to the town hall.''



\emph{Oh shit}.  If Coil had something for us to do-



I stepped away, thinking of a way to formulate an excuse.  I saw his forehead creased with worry.  As thin as he'd been before, he looked thinner now.  Looked years older, wounded, tired, lonely.



``I'll see you then, then,'' I told him.



``See you,'' he said, smiling sadly.  No pressure to stay.  He had no idea what was going on, I hoped, but he was still letting me do what I needed to.



I felt the need to reward him, to express some kind of gratitude, but I had only one thing to offer that he really wanted.  ``I-  don't know when.  But maybe I'll come home?''



Vague, again.  Just like with what I'd said before, there was no set date.  I'd said the exact same thing when I'd left in the first place.  It was almost an insult.



But I saw him smile.  ``Anytime, any day.  But we can talk about that over lunch, day after tomorrow.''



I nodded and turned to leave.  I wasn't half a block away from the house before I felt the tears welling up, running down my face.



I couldn't say whether they were because of my love for my dad or my despair for Dinah.





