





``Knock, knock.''



Triumph turned around.  ``Sam.''



She poked her head around the edge of the door, hand over her eyes.  \emph{Beautiful}.  She was blonde and wearing her skintight costume.  She had the figure to pull it off where so few really did.  The kind of body someone \emph{worked} for.  Her mask was off, tucked into her belt.



``You decent?''  Prism asked, not moving her hand.



``Yeah.''  He finished folding his hospital gown and draped it at the foot of the bed. Not perfect, but it was better than leaving a mess.



``You're okay to be up and about?''



``Yeah,'' he said.  He didn't want to reply with a single syllable again, so he turned to face her.  He smiled a little.  ``I'm tough.''



``Don't boast.  I was with your family while we watched the paramedics cart you off.''



``I made it.  I don't heal that much faster than normal, but I do heal faster, I don't scar, and I don't tend to suffer long-term injuries.''



``But you nearly died.  Don't forget.''



``I definitely won't forget, believe me,'' he said.  He balled up his bathrobe and put it in the gym bag that already sat on the bed.  ``I'm surprised you came.''



``We're dating,'' she said.



``Three dates, and we both agreed it wouldn't be anything permanent.''



``You say that and then you invite me to meet your parents.''



``Because the food at home is better than the rations you'd get anywhere else in this city.''  He raised an eyebrow, ``But you're the one checking on me this morning.  Didn't you have a flight?''''



``A flight's easy enough to postpone when the Protectorate's arranging it.  I decided I needed to sleep in after being up all night getting x-rayed, Ursa said she was ok with it.''



``I'm just saying, you didn't have to stop by.''



``Don't flatter yourself.  I wanted to see how Cache was doing.  It's a walk down the hall to see you.''



``Ouch.  Allies before guys?''



``There's got to be a better way of saying that.''



``Probably.  How's he?''



``Burned badly, but he's healing.  We'll see how bad the long-term damage is.''



``And how are \emph{you}?''



``Bruised, bit of a limp.  Pretty okay overall.''



``Good,'' he smiled.  ``Want to go get some coffee?  I've been running on so much caffeine lately that I think I'll pass out if I don't get my morning dose.  I'll lend you my shoulder so you don't have to put too much weight on that leg.''



``Coffee's good.  But are there any places that are open?''



``There's a place in the building.''



Prism made a face.



``Not institution coffee.  An actual coffee bar as part of the cafeteria.''  He slung his bag over one shoulder and offered her an arm.



``Don't you need a wheelchair?  I thought it was hospital policy to wheel you to the door.''



``It's fine.  Benefit of having a small hospital as part of the PRT building.  Pretty common for us to go straight from here to our offices, and there were apparently issues with photographers taking pictures of heroes in wheelchairs as they left the hospital.  Director Piggot arranged things this way for exactly this reason.''



``Damn.  Need to push for something like that in NYC.  Our hospital's off-site.''  She put a hand on his shoulder and they began making their way down the hall.



Ursa Aurora turned the corner and spotted them.  Triumph could see the frown lines above the glossy black bear mask she wore, her obvious relief and the quickening of her pace on spotting him.  His heart sank. \emph{Something's happened}.  \emph{Or it's happening.}



``Guys!''



``What's wrong?'' he asked.



``There's an issue.  Division in the ranks.  Looking ugly.''



``The enemy?''



She shook her head.  ``Our guys.  And it's about you.''



That caught him off guard.  He shook his head a little; no time to get into the particulars.  He'd deal with the situation himself.  ``Lead the way.''



Despite the apparent urgency of the situation, they couldn't run.  Prism was hurt and the elevator was the fastest way to their destination.  Ursa went ahead to press the button while Triumph helped Prism limp her way there.



``\emph{Gentler},'' she hissed, after setting too much weight on her bad leg.



``Sorry.''



``I hate this, being injured,'' Prism mumbled.



``It's not too serious?''



``No.  Skitter tethered me to the roof so I dropped halfway, stopped, then cut the line so I'd drop the rest of the way.  Landed on my side.  But being hobbled like this, it brings back bad memories.''



He turned to Ursa as they approached the elevators.  ``Press both buttons at the same time, three times in a row for the emergency use.''



Ursa did as he'd suggested, and the button began alternately flashing yellow and red.  The doors opened almost immediately afterward and they gathered inside.  Ursa hit the button for the basement floor: the Wards' headquarters.



He glanced at her teammate.  It struck him that it was inappropriate to ask, but it also felt like Prism was inviting the question.  ``Would it be bad form for me to ask?  About the bad memories?''



Prism shook her head.  ``Ursa knows, and I've been working on getting over it.  I already mentioned my history in gymnastics.  My dad's a coach, had spent his entire life pushing me and my siblings to be on the Olympic level.  I sometimes thought it was the only reason he had kids.  I was pretty close to qualifying when I tore my ACL.''



``Ouch.  You didn't re-injure it last night?''



She shook her head, ``Hip, not knee.  Looking back, I think I screwed up my knee back then because my dad had pushed me too hard and too fast.  But I blamed myself.  I got depressed, stayed home instead of going to the gym.  Once dad and the sibs realized I wasn't going to come along anymore, I started to get left out of family events, left behind when they went out to eat after training.  It doesn't sound like that huge a deal, but gymnastics had become a core part of my life, and it was gone.  Everything fell apart.''



``I'm sorry.  I know better than to say that's not significant.  Believe me.  I've been there.''



She shrugged.  ``I guess I became my own family.  Found another pillar to build my life around.  But even if I have a high pain tolerance, having an injury like this reminds me of those days.  Puts me in a bad mood for a while.  So I'm sorry if I'm irritable.''



``I can deal.''



They'd gone out as friends, first, because they both had similar backgrounds, and segued into a casual relationship.  They had both been athletes, once upon a time.  She was an ex-gymnast, he had been a baseball player.  She'd triggered because of the aftermath of a career-ending injury.  He'd acquired his powers because he'd been perpetually second place, doomed to miss his chance, a mere hair from a career in the major league.



He knew how devastating that stuff could be when you'd made the sacrifices, given up most of your adolescence to succeed at something, only to fall short.



He'd turned to his dad for help, and his dad had delivered a small vial that was supposedly designed to force a state equivalent to a trigger event, without the necessary trauma.  Irony had reared her ugly head when the major leagues had mandated MRI scans to check for powers and maintain the integrity of the game, mere months after he'd gained athletic ability that would let him compete.



In a way, he was glad.  Not that he had been back then.  He'd been spoiled, a brat, entitled.  He was relieved he hadn't continued down that road, that he'd found a career where he was on something of an even playing field with his peers.



Not that things were perfect.



He could hear the arguing the second the elevator doors parted.



Miss Militia, Weld and Kid Win stood on one side of the room.  Assault was on the other side, perched on the edge of the terminal, with Clockblocker, Chariot and Vista at his side.



``-vigilantism!''  Miss Militia's voice was tight with barely controlled anger.



``There has to be an authority for us to ignore for us be vigilantes,'' Assault said.  His voice was calmer, but his body language wasn't.  He was tense, the hand that wasn't gripping the edge of the console was clenched into a fist.  ``There isn't.  Nobody's stepping up to enforce anything.''



``The PRT stands.  All of the watchdogs are in place,'' Miss Militia spoke.  ``You go out and do something without an official a-ok and people are going to notice that we're acting completely outside of the principles and rules the Protectorate stands for.''



``How?'' Assault countered.  ``Media?  In case you haven't noticed, a full third of this city is still lacking power.  The reporters that have stuck around this long are too tired and too low on resources to follow along.''



``Cell cameras,''  Miss Militia said.  ``People are watching and recording us every step of the way.''



``We'll be covert.  I'm talking a fast, hard hitting strike.  Attack is always preferable over defense.



``You're talking revenge,'' Triumph spoke.  He let Ursa support Prism and stepped forward to join the `discussion'.



``Revenge, justice, it's a pretty thin line.  But sure.  We can call it that,'' Assault said, leaning back a little.  He smiled a little at Miss Militia; there was now one more person on his side of the argument.



Triumph glanced around the room.  Flechette, Ursa and Prism weren't taking a side.  They weren't local, and the politics here would be intimidating.



\emph{Still}, Triumph glanced at Flechette.  \emph{She's been around a few weeks.  She should feel confident about voicing an opinion}.



Was she being neutral, or was she undecided?  Or was there another factor at play?



He felt so disconnected from the Wards, these days.  He barely recognized his old team.  Vista, Kid Win, Clockblocker\ldots he'd been their captain, not so long ago.



Miss Militia and Assault were looking at him, waiting for him to speak.  From Assault's confidence, there was no doubt he expected Triumph to take his side.



Instead, he commented, ``Just going by what I've heard, Assault's arguing we should take the fight to the enemy?  Without Piggot's consent?''



``Piggot has told us to stand down,'' Miss Militia spoke.  ``So we'd be going \emph{against} her directive.''



``They attacked one of our own.  \emph{Again},'' Assault said.  ``\emph{And} they broke a cardinal rule.  They attacked family.  You don't unmask a cape, and if you happen to discover their secret identity, you don't go after their family.''



``The family's testimony suggests that wasn't deliberate.  Skitter informed Trickster partway through,'' Weld said.



Clockblocker cut in, ``But we can assume she found out beforehand.  Unless you're going to suggest she figured it out on her own?''



``No,'' Weld replied.  ``It makes sense.  I suspect Tattletale could find out something like that.  I'd even believe she's found out all of our identities by now.  \emph{But} I'm saying Trickster wasn't in the know, and he's the person who made the conscious decision to attack Triumph's sister.''



``They've broken other unspoken rules,'' Assault said, looking at Triumph and Miss Militia rather than the junior members.  ``Shatterbird?  Are we really going to let that one slide?''



``Anything goes when fighting the Nine,'' Miss Militia said.



``The Nine are gone.  He's still breaking the rules.  He kidnapped and took control of Shadow Stalker.  He's affected civilians.  Criminals, admittedly, but still \emph{civilians}.''



``And the people in charge know that,'' Miss Militia said.  ``If they decide that it's crossing the line, we can act decisively.''



``People in suits,'' Assault said.  ``They sit in offices with padded chairs, viewing everything through the filter of clinical, tidy paperwork.  They don't know what it is to be in the field, to face the risk of death or \emph{fates worse than death} in the service of this city.''



If Miss Militia had been getting ready for a response, she hesitated when Assault said `fates worse than death', his voice revealing a tremor of emotion.



Triumph could imagine the scene as he'd glimpsed it: Battery on her deathbed, wasting away from a poison designed to be cruel rather than efficient.  But as slow as it had worked, it had proved incurable.



Assault went on, and there was no hint of the earlier emotion in his voice.  Rather, he sounded dangerously like a leader.  ``If \emph{we} don't act on this, if \emph{we} don't move on the Undersiders and the Travelers, then we're saying that's alright.  We're saying it's okay to do those same things to \emph{us}.''



``You'd be violating your probationary status on the team,'' Miss Militia said, quiet.  ``Going against orders.''



``My joining the Protectorate was conditional on being on the same team as Battery,'' Assault replied.  He met Miss Militia's eyes with a level stare, as if challenging her to press the issue.



There was no doubt what was at the root of Assault's anger.  Miss Militia, by contrast, was the leader of the Protectorate because of her unwavering loyalty and willingness to not only abide by the rules but to fight for them.  Triumph could understand why they'd taken the positions they had.



He glanced at the others.  Weld was a company man, so to speak, and the PRT was his family, after a fashion.  It made sense that he'd stand by the rules imposed by the PRT, the Protectorate and the Wards.  Clockblocker had always chafed under the yoke of the institution, and Chariot could easily be the same.  Most Wards went through a phase like that, feeling the pressures, the strict rules, realizing that the Wards existed in part to keep them \emph{out} of the worst of things, while aching to go out and be a hero.  Clockblocker had never entirely grown out of it.



It could be that Chariot's stance here was what Coil \emph{wanted}.  Triumph couldn't forget that Chariot was an undercover operative, planted by the supervillain to gather information.



No, none of those calls surprised him.  The outliers, the ones that caught him off guard\ldots



``Vista, I didn't think you'd be wanting to break the rules like this,'' he commented.  Before she could reply, he said, ``And Kid Win.  I took you for more of a rebel.''



``I'm tired of losing people,'' Vista said.  ``We lost Gallant.  Aegis too, and Velocity, Dauntless, Battery\ldots''



``Yeah.  And Shadow Stalker,'' Triumph offered.



``She left,'' Clockblocker said.



``I'd still consider her a casualty,'' Triumph said.  ``We might not have \emph{liked} her, but she was one of us, and the enemy basically took her from us.''



``I don't want to forget Glory Girl and Panacea,'' Clockblocker said.  ``She and her sister did me a life-changing favor.  We don't know the whole story there, but the Undersiders or the Nine had to have played a part in how that unfolded.  But that's one hell of a list of names.  There's less of us than there are \emph{them}, and we're \emph{losing}.  Not just fights, but we're losing this war.  Don't you see that?''



``I see it,'' Miss Militia said, her voice particularly quiet compared to her raised volume earlier.  ``But that's exactly why I'm telling you not to do this.  The second we make this into an actual war, we change it from a losing fight to an outright defeat.  At best everyone involved would lose out, our enemies included.  I don't want that.''



``You're making it sound more complicated than it is,'' Assault said.  ``I'm talking a quick, hard hitting strike against one of their territories.  One of the master-classifications would be a good bet.  I'd suggest Regent, but Shatterbird is too big a complication.  Better to take out Hellhound or Skitter.  Doing either would cut their tactical options down by a third, and it could gain us a hostage to leverage against the others.''



``Not Tattletale?'' Clockblocker asked.



Assault shook his head.  ``She'd know we were coming.  It's in Armsmaster's notes from his first meeting with Skitter.  It's why they're so elusive as a group, and \emph{that's} why it's so crucial \emph{we} strike first, while they're still split up in individual territories.  Grue, Trickster, Genesis or Imp would escape too readily, and confronting Ballistic or Sundancer would place our side at too much risk.''



``They'd retaliate,'' Miss Militia said, ``And we'd almost certainly lose.  We're roughly matched in numbers, we're outmatched in raw firepower and they have the edge on us in terms of tactical knowledge.''



``So we're supposed to sit here and take it?'' Clockblocker asked.  ``If my family gets attacked next time, I don't think my dad's about to haul out a shotgun to defend himself.''



``That's not exactly how it played out,'' Triumph said.  ``But no.  I don't think we should take it, and I don't think we should attack.  Miss Militia's right.''



Assault's eyebrows rose in surprise.



``Thank you,'' Miss Militia said.  ``I understand that some of you are upset.  We're \emph{all} upset.  We're all concerned about our loved ones, about the current state of things in the city and about possibly being captured and controlled by Regent.  But we're only going to succeed with the support of the Protectorate as a whole, and we'll only have \emph{that} if we stick to the rules.''



``Well said,'' Director Piggot spoke.



All heads turned.  Director Piggot stood in the doorway that led to the stairwell.



``Director,'' Assault said.  He didn't look fazed by the woman's appearance.



``I hope you'll hear me out before committing to a plan of action?''



``Of course.''  Assault leaned back, folding his arms.



``Then let me introduce our visitors.''  Piggot stepped to one side, shifting her prodigious weight out of the way of the door.



There were two of them, each covered head to toe in power armor that was similar in theme, if not in design.  It was heavy duty stuff, and even without tinker abilities, Triumph could admire it as something exceptionally well made.



They were the same height, a man and a woman.  The man held a spear that was no less than fifteen feet long, with a two-pronged tip on the end.  The woman wore something that looked to be  a modified jetpack, divided into two pieces that each had to weigh as much as she did.  The exhaust jets fanned out to either side of her, like the feathers of a bird's outstretched wings.



The woman removed her helmet, then shook her head so her dark hair could fall around the armor around her shoulders and neck.  She wasn't beautiful, but she wasn't ugly either.  Even `plain' wasn't the right label.  She was exceptionally average in appearance, to the point that it was borderline eerie.  He couldn't pin down as belonging to any particular ethnicity, nor could he eliminate her from one.



\emph{Yet she's strangely familiar,} Triumph observed.



Triumph looked at the man, waiting for him to remove his helmet, but he didn't.  The man folded his arms instead, still holding on to the spear with one hand.



\emph{That body language}.  Triumph's eyes widened behind his visor.  \emph{No.  No way.  No way he'd come back here}.



But if he was here, then the woman would be-



``Dragon,'' Miss Militia said.  ``It's nice to finally meet you.''



Dragon extended a hand, and Miss Militia shook it.  ``Likewise.  Let me introduce Defiant.''



Triumph glanced around at the others.  Nobody here was so stupid as to miss what was going on.  Even the capes that weren't native to Brockton Bay would figure this out in a heartbeat.



``Dragon and Defiant have stopped by to pick up resources and gather information before taking on a long-term mission,'' the Director explained.  ``Would you like to explain?''



``The Nine,'' Dragon explained.  ``We know their general behavior.  After a spree like the one they had here in Brockton Bay, they're going to retreat.  They'll stick to back roads and isolated small towns, use time and distance to let the heat dissipate.  Jack may keep his people engaged with games like what he tried to set up here.  Scaling up slowly in a remote area, seeing how badly they can terrify the local populace, ending with a grand climax before moving on.  They'll also be looking to recruit and replace missing members, and I expect they'll go easier on testing the recruits until they've replenished their numbers.''



``What are you doing, then?'' Assault asked.



``We're going after them,'' Defiant spoke.  His voice was partially altered by his helmet, but it was still identifiable.



\emph{Why is everyone pretending they don't know that's Armsmaster?}



Defiant continued, ``And we're not going to stop.  Pursuit will continue twenty-four seven, year-round.  We keep them running until they get tired and hungry enough that they make a mistake, and we capitalize on that.''



``We've tried this before,''  Miss Militia responded.  ``I'm not saying I don't appreciate the idea, but Assault was just arguing that it's easier to attack than to defend, and I agree.  You won't be able to prevent every casualty.''



``The primary issue before,'' Dragon replied, ``Is that the previous efforts were squads, sleeping in shifts, always moving.  Invariably, the Nine would catch on to what was happening, they'd take out the squad on duty and then they would disappear before the others could mobilize to stop them.  Or the Nine would circle around and kill the off-duty squad members.  We don't have that problem.''



``I don't follow,'' Assault said.



``Dragon mentioned to me once that she doesn't need to sleep.  A side effect of her powers,'' Miss Militia said.



Dragon dipped her head in a nod.  ``I tried going after the Slaughterhouse Nine before, but Shatterbird's powers proved too difficult to work around, and I was only one person.  Now I have a partner.''



``Defiant?''  Miss Militia asked.



Defiant tapped his chest.  ``With Dragon's help, I've replaced my internal organs and parts of my brain with artificial equivalents.  My current downtime is a rough fifteen minutes a day. That includes waste, sleep and eating.  In the next two weeks, I intend to reduce it to a mere twelve minutes.''



Vista's hands went to her mouth in shock.



\emph{He's made himself into a monster.  And Dragon doesn't even flinch as he announces it. }Triumph's own eyes were wide.



Miss Militia seemed to recover faster than anyone else.  ``That's not the only issue the squads faced.  There's the psychological strain.  Hunting a prey for days, weeks, \emph{months} at a time?  Especially targets that will commit atrocities if you let your guard down for a second?  It gets to you.''



``I think,'' Defiant paused, as if he had to pick the right words, ``My single-mindedness will be an asset on that front.''



``It's worth a try,'' Dragon said.  ``Between us, Defiant and I can customize our equipment and approach to effectively counter the Nine's powers.  Once we have a lead, we'll maintain constant pressure for as long as necessary.  Even if we can't save everyone, even if we can't stop them outright with Siberian rendering others invincible, I think we can keep them from setting up another major event like they tried here in Brockton Bay, and we can hopefully keep them from recruiting.''



``The PRT is hopeful,'' the Director said, ``They gave their consent.  But you'll have to explain how this is relevant to the current situation.''



``Of course.  If everyone would turn their attention to the monitors?''



Assault had to hop down from where he was sitting on the edge of the long desk to see.  Everyone else turned as the images appeared across the screen.  One armored suit after another.



``The Cawthorne mark three.''



A sleek model resembling a cross between a dragon and a fighter jet, mounted with four engines around the `shoulders'.



``The Astaroth-Nidhug hybrid, making use of the Nidhug design that was partially damaged in prior confrontations.''



It didn't look like a mesh.  It looked like a cohesive design, a massive gun barrel with teeth at the end, outfitted not with a handle, but three afterburners at the rear and three at the midsection.  The landing gear looked spindly.  It was also, Triumph realized, quite large.  No smaller than a commercial aircraft, if the machinery beneath it was supposed to be a forklift.



``The Ladon-Two.''



It didn't look as sleek or combat-ready as the others, smaller, almost spherical in the body.



``That's a utility design,'' Chariot said.  ``What's the concept?''



``A forcefield generator,'' Dragon replied.  ``Dual offensive and defensive use.  I also have the Glaurung Zero-Model, the Pythios-Two, the Melusine-Six and the Azazel ready for field use.''



The camera panned out to show a sheared-off mountaintop with the seven armored suits and a hangar or factory.



``It is thanks to Defiant's assistance that I can now do \emph{this}.''



Simultaneously, each armored suit flared to life and took off, disappearing from the camera's field of view.  The cloud of dust and snow that spread out from the takeoff point obscured the camera's view.  The image went black.



``I have nine models in total that I can keep active simultaneously.  More are in development.  It's inefficient and expensive to keep all of them active when we do not yet have a bead on the Slaughterhouse Nine.  With the Director's consent, we'll be stationing the seven suits we're not personally using in Brockton Bay.  The PRT will remain in contact with me so I can remotely deploy them.  That is, those not already in use against the Slaughterhouse Nine or an Endbringer.''



\emph{Not just one, but seven suits crafted by the best tinker in the world}.



Triumph glanced at Chariot.  The boy seemed pensive, but that could have been one tinker admiring the work of another.



``Hard to believe you need Defiant riding along when you have that kind of raw firepower,'' Assault commented.



``Two sets of eyes are better than one, and we can keep each other sane.  Defiant will pilot the Uther when he isn't on the ground.''



``Well, Defiant, your hard work is appreciated.  I wish you the best of luck.  You too, Dragon,'' Miss Militia said.



\emph{They can't possibly be buying this}.



``Nobody's going to say it?''  Triumph asked, before he could censor himself.



Every set of eyes turned to him.  He could only go forward.



``You\ldots don't really believe this?  This Defiant thing?  He's not even \emph{trying} to hide it.''



The tension in the room was so thick he could have choked on it.



``If you have a valid concern about Defiant,'' Director Piggot spoke, ``I think it would benefit us \emph{all} to hear it.''



He opened his mouth to speak, but she'd already raised her hand to stop him.  ``\emph{Rest assured}, Triumph, if you were to allege criminal activity, we would arrest and detain him until a case could be made.  We'd pull him off this wholly voluntary task and if your charges were serious enough, send him to the Birdcage.  I suppose we'd have to adjust Dragon's battle plan against the Nine, she would likely be forced to rethink her idea of having the suits stationed in Brockton Bay, so she was better able to defend herself.''



``I get what you're saying.''



``I'm not saying anything, Triumph, only that you're entirely free to speak.''



He glanced around the room at the others.  Clockblocker looked at the monitors, Assault was adjusting his glove, Vista staring hard at the ground.  Nobody met his eyes.



Except Director Piggot.  It would have been easier to stare down a Bengal tiger than to meet her steel-gray eyes.



\emph{There's a difference between serving the system and enabling it}.



``Just wanted to say that the guy's got cojones,'' Triumph said, with no emotion or inflection.  ``Taking on the Slaughterhouse Nine like that, being this new to the game.''



``Quite so,'' the Director replied.  ``You'll be on double patrols until the elections are over, but you'll have the suits arriving within a minute of any confrontations.  The schedule's already in the system.  I and my direct subordinates will be available twenty-four-seven to those manning the console.  We'll then be able to verbally sign-off on the deployment of any of the dragon models.''



He couldn't bring himself to speak up and say it.  That Armsmaster was here, posing as a new hero.  Triumph knew he was enabling the system, he was allowing something wrong to happen here, but stopping the Nine was more important.  Having the suits to turn the table on the villains taking over the city?  Too much hung in the balance.



``Hey,'' Prism murmured in his ear.  She'd created a duplicate rather than hobble over to him. ``You okay?''



He shook his head.



``Still want to get that coffee?''



``No.  No thanks.''  He had trouble looking at her.  She hadn't said anything, hadn't \emph{tried} to say anything.  Yes, it was the better choice in the long run, putting Armsmaster to work against the Nine.  That didn't mean it wasn't wrong.



He was still relatively new to this.  Three years of duty, most of which had been spent among the Wards.  Was he the only one who was just old enough to speak out, not yet so old and jaded that he acceded to authority over anything else?



Or was it the opposite?  Was he of the age where he had the ignorance of youth coupled with the arrogance of adulthood?



As much as he'd thought she was the ideal girl before, as much as he'd shared her background with a failed sports career of his own, he could barely recognize her.



``I gotta go.  Need to take a walk.''



``My flight is-''



``Right.  Of course.  Have a nice flight.  Maybe I'll see you at a future date?''



Disappointment crossed her face.  ``Maybe.''



He stepped into the elevator and pressed the button.  The doors whisked shut.



His mind was a dull buzz as he walked.  He'd looked up to Armsmaster, once.  He'd \emph{understood} the man.  His own experiences of being second best in baseball ran parallel to the feelings Armsmaster had hinted at but never outright stated; the Protectorate captain had been resentful of Dauntless' meteoric rise, the inevitable moment that Dauntless would effortlessly supplant him as leader of the team.



As much as he hated to admit it, Triumph could understand where Armsmaster was coming from.  He could imagine the selfish joy the man must have experienced when Dauntless fell.  It would have been horrifying, too, no doubt, but that horror would be tempered by pragmatism.  Death was a natural consequence of an Endbringer attack.  It was reality.  So maybe Armsmaster had told himself it was okay to feel relieved that a rival had fallen.



He could see why Armsmaster had taken the route he had in the actual battle.  Taking on Leviathan one-on-one had been the only way the combat prediction program would work, and he'd had an effective weapon.  If villains happened to die in the process, well, he only had to call on that pragmatism again.  Triumph didn't agree with the line of thinking, but he could see how it had happened.



Armsmaster had been injured by Leviathan and Mannequin, and replaced parts of himself with mechanical equivalents.  He'd realized the benefits, worked with Dragon to step them up further.  He'd failed to defeat Leviathan, had been too hurt to fight the Nine directly.  So he augmented himself further, eradicated his need for sleep, for time spent eating and shitting.



Armsmaster, \emph{Defiant}, would achieve that respect he hungered for by stopping the Nine.  Or he would join Dragon in stopping an Endbringer.



It spooked Triumph because he could imagine it all too easily, where his teammates seemed dumbfounded.  It all made \emph{sense}, to the point that he could imagine himself doing something similar if he found himself in Armsmaster's shoes.



He wouldn't ever do something like that; that was how he'd reassured himself.  He was no longer that selfish teenager who'd received superpowers from his father like his peers got cars on their sixteenth birthday.  He'd hoped for an undetectable, undeniable advantage over his peers and been enraged when it had been denied him.  He'd changed, forced himself to change; he would be a good student, he'd help his fellow citizens, do the right thing.



Except he hadn't.  He'd kept his mouth shut.  Armsmaster would get away scott free with what he had done.  He might even succeed in stopping the Nine, in seeing them killed or put in the Birdcage.  The world would be better for it, and a warped man who'd mechanized his humanity for \emph{one more edge} would be regaled as a hero.  And he couldn't help but feel that he'd taken one small step forward on the very same road that Armsmaster had traveled before him.



Triumph's walk brought him to the scar.  Just as Leviathan had turned a section of Downtown into a sinkhole, the Director had dropped countless tinker-made bombs on central downtown.  There was radioactive fallout, but the reported levels weren't dangerously high.  Fire still burned in one area days after the fact, and he had to skirt around a cloud of dangerous-looking white vapor to reach his destination.



Seating himself on a safe-looking piece of rubble, Triumph rested his elbows on his knee and stared at the figures.  Crawler and Mannequin, turned to silicon by the detonation of one of Bakuda's bombs.  Crawler looked almost joyous, limbs spread and flexed, mouth open in a roar.  Mannequin was caught mid-dash, low to the ground.



He stared at them, as if he could burn them into his memory.  He couldn't say why he was here, exactly, but he'd felt compelled to see the real monsters for himself, outside of the heat of battle and the frantic and desperate scramble for survival.



Maybe it was to find some clue, some sign he could watch out for, that would let him identify the monsters from the men.



He'd stay for five minutes at most, he told himself.  Whatever the records said, it was better to be safe than sorry when radiation was involved.  Five minutes, and if he couldn't see anything by then, there wasn't much use in staying longer.



He stayed for fifteen.





