





The noise of the microwave beeping jarred me from the first restful sleep I'd had in some time.  I moved my head, and my pillow moved in response.



``Tried to tell them to stay quiet,'' Brian said, his voice low, ``They're not the most considerate pair in the world.''



``Muh?'' I mumbled something, and even I wasn't sure what I'd intended to say.  I'd been deep in the throes of some dream that felt strangely familiar, and I'd been pulled out of it quickly enough that I felt momentarily disoriented.  I wiped at my mouth where I'd drooled a little, and was suddenly aware that Brian was there.  I felt my face heat up as I realized I'd been leaning -and drooling- on his arm.  Alec and Aisha were unmasked and rifling through the `kitchen' to find something to eat.



Brian and I both spoke at the same time, with me mumbling something to the effect of, ``Sorry, I must have fallen--'' before shutting my mouth.



He waited, giving me a chance to talk as he wiped at the damp spot on his arm, then finally broke the awkward silence with,  ``I'm glad one of us slept.''



``You didn't?''



``Not a wink.''



He did look tired.  Not just like someone who had spent the night sitting upright, but like someone who had just finished a swim from one edge of the bay to the other.



``I hope I didn't keep you awake by leaning on you.  Don't even know when I nodded off.''



``It wasn't you, and I didn't mind.  It was\ldots'' he searched for the word.  ``Okay.''



\emph{`Okay'.}  How was I supposed to interpret that?  Or did he intend for it to be vague and noncommittal?



I shouldn't even have been worrying about that.  I blamed the fact that I was just waking up.  Brian was in a bad state.  Was there something I was supposed to say?  Something I should do?  Every gesture that normally demonstrated caring or sympathy or whatever else was a tender point for him.  A touch on the arm was an invasion of his personal space, which he was keenly aware of at this point.  Asking how he was doing was a reminder that he wasn't ok.  Would offering to help him out or giving him support make him feel more powerless, like he'd felt when Bonesaw had gone to work on him?



No.  That last one was probably okay.  ``You want anything?  Breakfast?  Coffee?''



``Coffee, please.''



I nodded, stood and rolled my shoulders.  Outside of the fact that none of the sleep I'd picked up over the previous night had been in a bed, I felt recharged.  Scrapes and bruises I'd only been dimly aware of were gone, as were the more obvious, attention-grabbing injuries.  That, in turn, made me think of the circumstances that had led to my good night's sleep and healing job.  It was bittersweet.  Like a young child that was being forced to stand in a corner, feeling as low as she ever had, her stomach full with the entire birthday cake she'd just devoured.



Okay.  Still a little out of it.



I joined Aisha and Alec in the kitchen.  ``Morning.''



``Sup,'' Aisha said, curt.  She'd found some frosted cereal and was pouring herself a bowl.  She gave me a sidelong glance that wasn't so flattering.



``How is the man?''  Alec asked.



``Stressed, anxious, not sleeping.  Can't blame him.''



``And you're using all that to get closer to him?''  Aisha asked.



I blinked.  ``No.''



``Looked awfully cozy,'' she replied.



I glanced back in Brian's direction.  He was standing at the window at the other side of the building, peering outside, his back to us.



``I drifted off.  An accident.  Trust me when I say I feel bad enough about doing \emph{anything} to make him feel less than a hundred percent comfortable when he needed rest.''



``Bet you a thousand bucks he didn't mind,'' Alec said.  Aisha gave him a dirty look.



``He's nice enough that he wouldn't want to disturb me, even feeling like he does right now.  He must have gone out of his way to stay still.''  I didn't look at either of them as I filled the kettle the rest of the way and put it on the stove.



``Sure,'' Alec drawled.  In a more normal voice, he said, ``But what I'm saying is he wouldn't mind.  Now, it's been a little while, but there was a time when I had someone in my bed every night.''



``When you were with Heartbreaker,'' I said.  From the look of disgust on Aisha's face, and what I imagined was a similar expression on my own, I suspected we were on the same page.  At least on this one thing.



``Sure.  Cape groupies, my dad's girls, people I used my powers on toward the end.''



There wasn't even a trace of guilt or shame on his expression, no regret in his tone.  He just looked bored.



He went on, ``What I'm saying is that I'm speaking from experience.  Having someone cuddled up beside you, even if it's a little bit of a pain in the ass, having that body contact isn't so bad.  Especially when you've had a bad day.''



Was that Alec trying to be supportive?  I glanced at Aisha, and she gave me something of a dirty look.



I was awkward, screwed up and feeling guilty on a lot of levels, from Brian to Dinah to the people in my territory that I hadn't seen to.  Brian was traumatized, and that was layered on what he'd described to me as an unfamiliarity with social situations and emotions.  Alec was fucked up in a way I couldn't even label.  Aisha wanted to protect her brother but didn't know how, lashing out at me instead.  Damaged people.



Much of the water in the kettle had been heated, already, and it didn't take long to boil as we got our individual breakfasts together.  I took it off the stove and began preparing Brian's coffee and my tea.  After a moment's consideration, I began preparing bacon and eggs, and rummaging around for toast, bagels or english muffins.  I'd use whatever I found first.



Tattletale, Bitch and three of the dogs came in through the front door.  I didn't miss how Brian turned to face the door, tendrils of darkness creeping through the gaps between his fingers and crawling up his arm.  It took him a second to relax.  Tattletale threw me a package.  I opened it and found a pair of glasses.  I slid them on.



Leaving the food cooking on the stove, I brought Brian his coffee.  Maybe some normalcy would help.



``Morning,'' I said.



``Morn,'' Lisa replied.  ``We were out making sure there wasn't trouble.  Very, very quiet, after the last couple of days.''



Rachel glanced at me but didn't say a word.



``Want food?''  I offered.  ``I've got some stuff on the stove.  There's some bacon if you want to give some to the dogs, Rachel.''



``It's bad for them.  And I don't give my dogs human food.''



``Right.  Thought they might want a treat, sorry.''



``But I'll have some,'' she said.



``Cool.''



I returned to the stove and started preparing breakfasts.  I served Brian first, then prepared some toast and bacon for Bitch and some scrambled egg for Lisa.  It was almost a relief, having something concrete to do, a way to help, when I didn't know how to act around Brian.



By the time I had Bitch and Lisa served, the Travelers had been roused by the smell of breakfast.  I offered them some breakfast, and Ballistic took over at the stove to cook for his team.



We arranged ourselves on the ground floor, Alec and Aisha sitting on the stairs, Lisa and I sitting on the couch, and Brian in the corner by the window, looking distracted.  Bitch seated herself on the floor, her back to the wall, her dogs at her side.



While we waited for the Travelers to get settled, I asked, ``I've been meaning to ask.  What \emph{is} Bastard?''



``You mean what breed is he?'' Aisha asked.



``No,'' I said.  I left it at that.



``He's a wolf.''  Bitch scratched the skin at his shoulders, digging deep.



``No shit?'' Alec said.



``Where do you even find a wolf?'' I asked.



Bitch didn't venture an answer, so Lisa spoke, ``She didn't find him.  He was a gift.  And since it didn't come from Coil, that means--''



``Siberian,'' Bitch finished.



``That's crazy,'' I said.  \emph{How long has it been since we had a chance to talk and touch base like this?}  ``She's crazy powerful.  Majorly scary.  And she just, what?  Handed you the wolf cub and told you that she's picking you to be a member of her team\ldots how?''



``She told me with words.''



``She doesn't talk,'' Brian spoke up.



``She \emph{told} me,'' Bitch repeated.  ``She showed up, I tried to fight her, didn't work.  She explained, she left.  Left the cub at my place.''



I saw Lisa glancing between Bitch and me with a curious look on her face.  When I raised an eyebrow at her, she shook her head a little and then turned to Bitch, ``That's potentially a problem.  What's to say Bonesaw or Mannequin didn't put some sort of tracking device in him?''



``They didn't,'' Bitch said.



``How can you be sure?''



``He smelled like the forest when I got him.''



``It would have taken them \emph{seconds} to stick it in him.  It would mean there was a way to find you.  Find \emph{us}.''



``No.  Doesn't make sense, what she was talking about.  Being free.  Accepting that we're animals.''



``I wonder about that,'' Lisa said, pulling her feet up so she was sitting cross-legged on the sofa.  ``Maybe she was playing you?''



``Is she really that smart?'' Alec asked.  ``\emph{Jack} is smart.  Bonesaw, Mannequin, sure, to varying degrees.  But Siberian?''



``My instinct?'' Lisa shrugged.  ``She's an actor.  Playing up the feral angle, hiding a deeper strategy.  She might even be playing a long con on her team.  Or maybe her intentions are pure but she's keeping them in the dark about the key stuff.''



``Like?'' Trickster asked, as he found a seat on the arm of the chair Sundancer was sitting in.



Lisa said, ``Brian's new powers.  He was copying powers from the people who were in the darkness, yeah?''



Brian nodded.



``He got the ability to grant healing from Othala.  Regeneration from Crawler.  But who was the shadowy figure he used to pulverize Burnscar?''



``You're thinking Siberian,'' I said.



Lisa nodded.  ``Sure.  What if she's like Genesis?  Or Crusader?  What if Siberian has a very real, vulnerable human body somewhere nearby, always has, and the body she's using is a projection?  Maybe it's something even Jack doesn't know.''



That gave us pause.  An in.  A way to stop the unstoppable beast-woman.



``No,'' Bitch clenched her fist, and I could see her dogs responding to her body language, tensing.  ``Don't buy it.''



``Why not?''  Lisa asked, her voice gentle.



``What she said made too much sense.  She said things and she \emph{understood}.  I'm fucked up.  I know I'm fucked up.  Not good at dealing with people.  But I could deal with \emph{her}.  I understood her.''



``That doesn't mean she didn't lie, Rachel,'' Lisa said.  ``It only means she understood you well enough to know how to deceive you.''



``No.  It's not--''  Bitch stood abruptly, and Bastard yipped.



``Rachel,'' Lisa tried, but Bitch turned away.



``There's one way we could try to find out,'' I said.



Bitch turned at me and glared.  There was a viciousness in the look that I couldn't blame entirely on her grudge against me or the current conversation.  Just like Brian, there was a minefield there.  I couldn't hope to guess at what would press her buttons.



``You'd want to know, right?'' I asked.  ``You wouldn't want to give her the benefit of a doubt if she was playing you.''



``You assholes are saying I'm gullible.''  If Bitch had hackles, they'd be standing on end.  Her fists were clenched at her side, her feet planted apart, as if she'd be ready to start swinging, whistling for her dogs to attack, at any moment.



``Hey,'' I raised my voice.  ``Answer the question!  Would you want to know?''



``Yeah, but--''



``Then we get in touch with Cherish.  We get an answer from her.  She'd know.''



``I'll get in touch with Coil, then,'' Lisa said.  She got up and headed into the room where she and Aisha had been sleeping.



I focused on my breakfast, hurrying to finish it before it got cold.  I'd been distracted by the conversation, and cold toast was depressing.



When I looked up from my plate, glancing at the others to double-check that they were okay, that I wasn't missing anything, I saw Bitch staring at me.



``You want more food?''  I offered.



``You mean what you said?''



\emph{About the food?}  ``I don't follow.''



``Last night.  You mean what you said?''



``You'll have to remind me.''



``You said something about doing the same thing for the rest of us for what you did for Brian.''  She broke eye contact, looking down at Bastard.



My fight with Brian.  ``You heard that.''



``Mm,'' she grunted.



I glanced at the others.  Trickster was talking with his two teammates, Genesis still elsewhere, and Alec and Aisha were talking.  Alec was apparently demonstrating his power, making Aisha's fingers twitch.  Brian looked on with a glower on his face, but I got the impression his attention was divided between that dialogue and my own discussion with Bitch.



``Yeah,'' I told Bitch.  ``We've been over this.  I really don't know how to make it clearer.  If it came down to it, I'd risk my life to save yours.''



``\emph{Why}?''



``I- I don't know if I can really say.  You're my friend.  We've been through a hell of a lot of crap together.  We back each other up because we have to.''



``You think I'd back you up?''  The question was a challenge, brusque, barely-but-not-quite-anger.



``Don't know.  Does it matter?''  I glanced at Brian.  He was paying attention to what I was saying.  I felt momentarily self-conscious, struggled to find words that wouldn't provoke a negative response from one of them.  I settled for a middle ground as I thought aloud.  ``Life's not fair.  It's not even, not balanced, not right.  Why should relationships between people be any different?  There's always going to be an imbalance in power.  The other person might have a higher social standing, they might have money, or more social graces.  Isn't it better to stop stressing about quid pro quo and just do what you want or what you can?''



``Words,'' Bitch dismissed me.



``Words, sure.  I'll make it simple, then.  I consider you a friend, I'll help you when stuff goes down.  And you\ldots do whatever you think is right.  Do what you want to do.  I won't stress about it, and unless you fuck with me like you did when we fought Dragon, I'm not going to hold it against you.''



She set her jaw, clearly irritated at the reminder.  Whatever.  I'd needed to make my point.



If she had been intending to give me a response, I didn't hear it.  Lisa ventured back into the room, and all eyes turned to her.  She held her hand over the lower half of the phone.



``For those of you who haven't been in contact with Coil, we ended up locking Cherish in an overturned boat's hold in the Boat Graveyard.  She's there now, with food and water, totally isolated, several layers of confinement, including but not limited to chains.  She wants to strike a deal, in exchange for details on Siberian and the Nine.''



``Letting her go?  No,'' Brian said.



``Not what she wants.  She just wants a chance to talk to us,'' Lisa looked at each of us in turn.  ``Two minutes to address us, and then she dishes out the dirt, gives us the location on the Nine, the details on Siberian and answers any other questions.''



``Nothing saying she'll tell the truth,'' Alec said.



``And she's in a position to say stuff that could create doubt or tension in our ranks,'' Trickster pointed out.



``True,'' Lisa conceded.  ``But here's the thing.  I'm getting the vibe she \emph{wants} us to turn her down, so we'll figure out the real scoop later and regret it.''



``What, you mean something like Siberian being \emph{here}?  `Don't you wish you'd asked me to tell you where she was, because she's standing fifteen feet away from you'?'' Alec asked.  ``Yeah, that sounds like my sister.''



``How sure are you?'' Brian asked Lisa.



``That there's more to it?  Seventy five percent, to ballpark it.''



``Bad idea,'' Brian said.  I found myself nodding in agreement.



Lisa raised the phone to her ear.  ``Nope.  Don't suppose we can change your mind?''



There was a pause before Lisa hung up.  ``Eighty-five percent sure there's more to this story than she's letting on.  She was all too okay with saying goodbye for someone chained up in a hot metal prison cell.  That, or she thinks we're going to call back.''



Sundancer spoke up, ``Can't we?  What are we really risking, here?  I mean, what's at stake?  The worst case scenario, if we let her talk?''



``Can't say, can we?'' Lisa said.  She tossed the phone in the air and then caught it.  ``Say one of us has something to hide that Cherish could reveal to the others.  Nobody's about to admit it.''



There were glances all around.



``But I think I have an idea.''  Lisa smiled.  It was her old smile.  The scar was there, but it no longer pulled her mouth into a perpetual half-frown.  ``Brian, got any books here?  Or magazines?''



``Upstairs.  Aisha, go grab something.  Any book on the floor of my room.''



``Why--''  She hesitated when she met his eyes.  ``Whatever.''



It was a minute before Aisha ventured back downstairs with a novel.  It looked like a suspense thriller.



``Here's the deal.  Everyone closes their eyes.  We close our eyes while the others take their turns tearing a page out of the book.  The higher the page number, the worse our inner thoughts and secrets.  The last page, Uh, three hundred and fifty-five, we'll say, is the worst of the worst.  Unforgiveable to the point that someone here would kill you and the rest would be okay with it.''



She rifled through the pages of the book, ``Anything below one hundred and fifty, it's tolerable.  Stuff we'd be ashamed for others to know, but we'd be okay with them knowing for the greater good.  We each stuff it in between the couch cushions, until we've got a crumpled mess and none of us know who tore out which page.  If we're more or less safe, if the numbers aren't too high and we think we can stand to have Cherish dish out the dirt on the others, we'll take her up on the deal.''



Nobody disagreed with the plan, but I supposed that doing so would look bad.  I closed my eyes as we went around the room, until Lisa tapped me on the shoulder and handed me the book.



Where did I stand?  What secrets was I keeping, and how highly did I value them?



I had my deal with Coil, with the real possibility that I might wind up his adversary.  Lisa knew that, as did Brian, but the others didn't.  I suspected that Aisha could be convinced to roll with it when Brian did, so long as we didn't push too hard.  Alec and Bitch would go with the majority.  The Travelers?  They had other stakes in this.  That was more dangerous.



One-sixty.  I tore it out and stuck it in the couch, sat down and handed the book to Lisa.



It took another minute for the rest to decide.



``So, in order\ldots twenty-six, one-twenty-two, one-forty, one-forty-one, one-fifty-five, one-sixty, one-seventy-five, two hundred twenty-two, and three-twenty-five.''



\emph{Three-twenty-five?}



``That's a no, then?'' Brian asked.



``Something like that,'' Lisa replied.  She picked up the phone and dialed.



``What are you doing?''  Trickster asked.  ``You said we wouldn't go ahead if we didn't all agree.''



``You're right.  But I'm going to try to haggle with her,'' Lisa replied.  ``Hello?  Yeah, you already know the answer.  No-go.  Uh-huh.  Sure.  What if I asked for the Travelers to leave?  You could address the rest of us.  You and I both know you're doing this to sate your boredom than for any grander purpose.''



There was a pause.



``Good.''  Lisa put her hand over the mouthpiece.



``Does that really work?''  Trickster asked.  ``What if we wanted to keep stuff from you?  She could tell you while we're out of the room.''



``\emph{Do} you want to keep anything particular from us?''



He shook his head.  ``But how do you know your teammates didn't pick the high numbers?''



``I don't,'' Lisa flipped through the pages.  ``But just going by what I know about our groups, I think our team is going to be more concerned about what outsiders think.  You guys are going to be more concerned about what your teammates think.  Am I wrong?''



Nobody spoke.



``We could do another blind vote,'' she suggested, ``In case anyone wants to say they're not cool with these new terms.''



``Speaking as the person who took two-twenty-two, I really don't care all that much,'' Alec said.  ``I picked a higher number because I thought it would bother those guys.  I figure my team knows enough.''



``Exactly as I said before,'' Lisa said.  ``Anyone else have any major objections?''



I shook my head.  I could deal with the team knowing about my plan.  If things went south, they'd find out anyways.



The Travelers made their exit, Shatterbird came inside to stand guard by the door, and the rest of us settled down.  Lisa dialed and put her cell on speaker phone.  It rang twice before Cherish answered.



``Finally,'' her voice came through the line.



``Your two minutes start now,'' Lisa spoke.



``I should get four, since I'm dealing with only one group.''



``One minute, fifty-five seconds,'' Lisa replied.



``Where should I start?  Hey, little brother.  Want me to tell them the sort of things you \emph{really} did when you were back home?''



``It's sort of tedious,'' Alec replied.



``I wonder.  Rape culture is a funny thing.  People gloss over some pretty shitty, creepy, \emph{wrong} behavior, little brother, when they know the person in question.  But you raise the reality of what they're doing, and it's a whole lot harder to shrug it off.''



\emph{Rape}.  It was a loaded word, but Cherish was right.  She was a horrible person, to be sure, but she was right.  Did I really want to face what Regent had done, before we knew him?  Rape.  Murder.  He'd said, this very morning, that he'd done what he did because he'd been young, but that was just an excuse.  The deeds were still done, the consequences very real.



``You're really one to talk, Cherie.  You've done what I've done, many times over.''



``I'm not pretending anything.  I am what I am, I don't put on a facade,'' Cherish retorted.



``That's a blatant lie.  If you showed your true nature to the world at large, your face would be too ugly to look at.''



``\emph{Ouch},'' Cherish layered on the sarcasm.  ``Don't think I don't know what you're trying to do.  You're delaying me, so I have less time to work with.  Why don't I get started?  Let's talk about your first kill?  Gang member, a kid.  You used him to kill his boss.  His older brother, in fact.  Because daddy wanted you to.  Then dad ordered you to kill him.  But you didn't make it fast, did you?  You made him stab himself with a fork, over and over, and over\ldots''



``Keeping in mind that I was hanging out with \emph{you} and the dirty old man and our brothers and sisters.  Nature and nurture, I was kind of fucked on both fronts.  It was a matter of self-preservation to keep you guys entertained, and that was the sort of thing you liked.  Sorry\emph{, }\emph{like}, present tense.''



``Maybe, maybe.  And the drugs?  When daddy had you practicing your powers, you `hijacked' a few people at a time, used their bodies to get high with no consequences for \emph{you}, you threw orgies for yourself\ldots''



``Again.  I was a kid.''



``How much does that excuse?''



There was a pause.  I looked at Alec, and he rolled his eyes at me.  Was he like Brian?  His emotions buried deep inside?  Or were they simply not there?



``What about darkness-boy?  Want to talk about what happened yesterday?''



I clenched my fists.  Lisa raised a hand, telling me to stop.



``You're running low on time, Cherie,'' Alec said.



``I'm happy for the chance to talk.  Bonesaw's alive, you know.  She has hands, borrowed from Mannequin.  She's plotting what she's going to do to Grue.  Think about that.  She's going to take him apart, and it'll hurt \emph{worse} the second time around, because she makes that sort of thing a matter of personal pride.  She's thinking about it, daydreaming on the subject, and she's a smart enough cookie that she'll figure it out.''



Brian turned his back on the phone, staring out the window.  I wanted to reach out to him, to help ease the weight that idea must have set on his shoulders, somehow.



``Bitch, you know that Skitter's going to betray you again.  Look at her.  She prides herself on being smart, and you know the best way for someone to make themselves feel smart? They make others look \emph{stupid, }and you're the stupidest person she has access to.''



I tensed.  I would have been lying if I hadn't said I hadn't seen something along these lines coming, but it ultimately depended on Bitch's reaction.



``I fucking hate people who try to manipulate me,'' Bitch growled.  ``Next time I see you, I'm knocking your teeth in.''



There was a pause.



``Ah well,'' Cherish said.



``And your time is up,'' Alec said.  ``So, now's the point where you fuck us over and don't say a thing.''



``Why would I do that?  I \emph{want} you to deal with the Nine.  You killed Burnscar, didn't you?  If you dealt with Siberian, life would be a lot easier for me.''



``So we're right?''  Lisa leaned forward.  ``There's a weakness.  She has a real body somewhere?''



``She does.  Right now it's actually not too far from you.''



\emph{Fifteen feet away}.  I remembered Alec's joke.



``Near that hole the Endbringer made,'' Cherish said.  ``Both of them, the real Siberian and the body.''



``You know what she looks like?''



``He.  A man.  Middle aged or older.  Unkempt.  Doesn't eat much, probably thin.''



That wasn't what I would have expected.



``Right now?  Siberian's chasing down one of the candidates.  She's taken on the next round of testing.  Simple test.  Hunt them down and if she catches you, you fail.  She eats you alive as punishment.  Wonder how many she can knock off before you take him down.  \emph{If} you take him down.''



``Who's she after?  We gotta know.''



``No you don't.  Way I figure it, you go into the fight blind, you still stand a pretty good chance of offing her.  No skin off my back if a few of you die in the process.''



``You need enough of us alive to deal with the rest of the Nine.''



``Maybe, maybe,'' Cherish taunted us with her tone.  ``But shouldn't you hurry?  The hero is going to die.''



It was Panacea or Armsmaster.  Both were complicated.  Panacea wouldn't be able to defend herself, but Armsmaster was a whole mess of complications.



We hurried to get suited up.  My mask in ruins, I wrapped a scarf around my lower face and covered it with bugs.  I drew them around my eyes to hide the frames of my glasses.



As I finished up, I glanced at Bitch.  Her knuckles were white, her posture rigid.



She was \emph{pissed}.



I made sure I had all my gear, then joined the rest in filing out.  Grue and Tattletale were the last out the door.



Glancing back to check on Grue, finding his posture and expressions unreadable beneath his darkness and costumes, I caught a glimpse of Tattletale messing with one of the pouches on her belt.  The pages we'd torn from the book were folded into a tight square, and she was pocketing them for later study.  She saw me looking.



``You going to be okay with this?''  She asked me.  ``You're the best equipped to find Siberian's real body and stop her.  Him.  Them.''



``I'll deal somehow.''





