





Amy Dallon ran for her life.  It wasn't the kind of run one saw in marathons or anything like that.  It was mindless, panicked, like a herd animal in a stampede.  She took the easiest and most obvious paths available to her, stumbling as often as not, her sole and all-consuming purpose being to put distance between herself and her pursuer.  Her left hand was cradled against her chest, the very ends of her pinky, ring and middle fingers missing.  Was that intentional?  Harming the healing hands?



Siberian didn't even have to run to keep up.  The chase was something she'd honed into an art.  Amy had to run around buildings, hurdle over piles of debris, and climb fences.  Siberian anticipated her movements, pushed through walls of stone, brick, wood and plaster as though they were tissue paper and ultimately took the shortest, most direct paths.  If Amy happened to get a little too far away, Siberian would use a short hop to cross half a city block, often crashing through a wall or the side of a truck in the process.



She could have closed the gap and gotten her hands on Amy at any moment, but she didn't.  She was a cat with its prey, and Amy didn't have anything that could help her get away.  Amy ran and created some distance, getting just far enough that she might think she'd escaped, then Siberian would appear in front of her, or to one side.  It happened once, twice, then three times.  Each time, Siberian drew closer.



The fourth time she closed the distance, she leaped up to a spot behind Amy and caught hold of Amy's wrist.  Amy jerked as the hold interrupted her forward momentum.  She screamed, her legs buckling under her.



Siberian took her time, grabbing at Amy's other wrist, then prying at her fingers.  Three were already missing segments, and Siberian seized the index finger.  Slowly, inexorably, she guided the finger to her mouth, her lips parting.  Amy thrashed, but couldn't free herself from Siberian's grip.



``Shouldn't we do something?''  Sundancer asked.  Her hand trembled as she lowered the binoculars.  I wasn't sure how useful Sundancer was going to be, on several levels.  Our group consisted of Trickster, Grue, Tattletale, Sundancer and myself, with two of Bitch's dogs to get us from A to B.  The seven of us were gathered behind the wall of a ruined building, a considerable distance from Siberian.



I glanced at Grue.  He was tense, rigid enough that I could see his stillness through the darkness.  \emph{Anything I'd say to him would hurt more than it helped}.  I turned my attention back to Amy and Siberian, looking through the binoculars.  Instead of addressing Grue, I told Sundancer, ``Nothing we can do.  But I think Siberian is going to-''



As if she'd heard, Siberian closed her mouth.  Amy recoiled with her whole body, pulling away, and Siberian let her go, giving her a little push.  As her quarry stumbled and started to run, Siberian simply stood there, waiting.



She wanted to give Amy a head start.



Amy wasn't bleeding as much as she should have been.  I knew she couldn't use her power to affect herself, or this fight would be playing out much differently.  But maybe she was using her power to affect microbes on her hands?  Changing them into something that could breed, coagulate, and staunch the wounds?



It was what \emph{I'd} be doing.



But I'd also be trying to use microbes to form some kind of defense.  I'd be reaching out for algae or other plant life I could use to obscure my retreat.  Something to produce an opaque gas, to block line of sight or give me hiding places.  Amy had far, far more versatility than I did, and I had little doubt she'd be able to mimic my power with a little time for preparation.  With some forethought, preparation and strategic thinking, she was capable of holding her own, getting away.  She had \emph{so} much potential.



But Amy Dallon wasn't that sort of person.  She hadn't gravitated toward front-line combat, nor had she gotten in any real fights, to the best of my knowledge.  When Leviathan had hit the city, she'd stayed behind to give medical care instead of using her power against him.  Now she was panicking, up against an unstoppable enemy and an inevitable fate, and she didn't have the tools, mental or otherwise, to hold her own.  Siberian would catch her and release her over and over, taking her apart piece by piece.  Eventually the blood loss would mean Amy couldn't run any more.



Or maybe Siberian was waiting for Amy to break, mentally.  How long could she put up with this before she lost all hope and surrendered herself to a fate of being eaten alive?



Using my power, I began to gather a swarm around Amy.  Her initial reaction was to freak out.  She thrashed, stumbled, and fell.  She landed in the shallow water with her good hand thrust out to prevent herself from landing face first.



Her second reaction, beyond the knee-jerk fear, was to use her power to start shutting mine down.



``\emph{Idiot},'' I hissed the word.



``What?''  Tattletale asked.



``I'm trying to save her life, and she's turning my power against me.''



Two ways this would go.  Either she clued in that I was trying to help, or she died.  I was \emph{really} hoping it wouldn't be the latter.  I didn't like her, but she didn't deserve to die.  There were very few people in the world who deserved to die like this.



I could feel a not-unfamiliar headache building as I leveraged my power to draw more of a swarm around her.  Siberian was watching, uncaring.  As was so often the case, my timing had to be specific.  She wouldn't let Amy go as a matter of principle, but she'd let hope dangle in front of both of us.  That penchant for offering hope and then dashing it was a weapon she and virtually every other member of the Nine had at their disposal, but it was also a tendency we could exploit.  A weakness, if you could call it that.



This would have been easier if we'd had another mannequin like we used in our first victory against the Nine, using Trickster's power to evacuate Amy, but we hadn't been near my lair and we'd used every mannequin we had in that fight.  We could have kludged something together, something vaguely Amy-sized and Amy-shaped, but time had been tight, and we hadn't found anything that would serve that would \emph{also} fit on the dogs.  Deploying on the one job with the explosives, mannequins and two or three people riding each dog had been our limit, before.



Siberian took hold of a length of her long hair and combed her fingers slowly through it, her back twisting and arching a little as she reached behind her head, the flank of her body exposed to the diffuse light of the overcast sky above.  If Cherish wasn't fucking with us, the \emph{real} Siberian was a middle-aged man.  What, then, was the projection?  Why was it female, when Brian's had been male and so very similar to him?  I would have asked Grue something to try to shed light on the subject, but I didn't want to get him thinking about what had happened back then.



My head was starting to pound, my power getting more sluggish.  Where possible, I used my bugs to find, catch and kill the bugs Amy had altered with her power.  It wasn't enough; my power was still getting steadily weaker.  Amy fell again, climbed to her feet and swatted her good hand through the swarm, disabling those bugs who stayed on her skin for any longer than a second.



It was also making it harder to sweep the area for Siberian's real body.  There were pockets of people here and there.  I needed to keep tabs on the ones who fit Cherish's description; middle-aged, male, probably unkempt, thin.  What made it trickier was that I had to find him without him catching on and sending Siberian after us.  There was one man nearby, but he was fit.  Another there: fat, startling and trembling at the distant sounds of Siberian tearing through the landscape in her pursuit of Amy.  I found another, but he was clutching a small child to him, and she clutched him back.  Father and daughter, no doubt.  The little girl wasn't Bonesaw, either.  Too small.  In the next cluster of people-  I had to stop and press my fingers to my temples.  It \emph{hurt}.  Damn that girl.



I had to cover her, though, so having my bugs near her was unavoidable.  Amy needed to be one-hundred percent out of Siberian's sight before we acted.  As if she was actively seeking to make things harder on us, she took a route that carried her out of sight of our binoculars, behind a building.  Not that she knew we were there.  It was bad luck.



I focused my binoculars on Siberian, instead.  Her hair drifted in the wind.  The length she wasn't holding in her hand fanned out, briefly.



``If the wind moves her hair like that, is that a clue?'' I asked, looking at Tattletale.  ``Like the dust on Glory Girl's clothes hinting that she wasn't covered by her forcefield?''



``Ninety-five percent sure I'm right on this score, but her power probably copies her real body's physiology to some degree, molding all the internal organs and whatever else with whatever reality-scrambling-stuff she's made of.  Her call about what parts of her are affected by what, so I don't-''  She stopped, ``Heads up.''



Siberian was letting her hair fall from her hands.  She flicked the last strand back over her shoulder.



I collected the swarm into a dozen decoys in the same instant Siberian started striding forward, then scattered them.



Siberian stopped, pivoting on the spot, then lunged for one side of the street.  She threw herself through the side of a parked pickup truck, shearing through the fiberglass and metal, and landed in a crouch on the far side of it.  She gripped the two sections of the vehicle, tearing where they were still connected on the underside, and then spun in place, holding each half out to one side.



I couldn't be sure, but as I looked through the binoculars, I was pretty sure that I caught a glimpse of her holding one half of the truck by a glass pane of a side window, index and middle finger on either side of the broken glass.



In most cases, a cape trying to pick up a car by anything but the undercarriage would find it falling apart, the weight of the vehicle pulling it free of whatever section the cape was holding.  Siberian didn't have that problem.  She simply extended her power through whatever she was holding to keep it intact.



With a throwing motion, she whipped one section of the truck over her head, hurling it forward so it crashed through no less than five of my decoy swarms.  She did a tight spin as she stepped forward and made the second throw into a smooth continuation of the first.



Her accuracy wasn't quite so good for the second hit.  It crashed through the water and hit the ground before it rolled out of my line of sight.  It was only through my swarm that I felt it hit Amy and my decoy swarms.  Most of the momentum was lost in the initial impact, and it didn't pulverize her.  She was in one piece, at least.



In retrospect, that might have been intentional on Siberian's part.



``She's advancing,'' Tattletale reported.



``Yeah,'' I replied, absently.  I was focusing on getting my bugs on site.  The bugs that had surrounded Amy and formed the decoys in her immediate vicinity were still there, and I gathered them into humanoid shapes again.  I didn't have line of sight to her, but I could feel them rising in what must have looked like a very human way.



I'd known that using the decoys would provoke Siberian.  She wanted to drive home that inevitability of her target's fate, and that meant she would stop playing around the second she thought Amy might really escape.  That was the bad.



The good side of things caught me by surprise.  As though a switch was flicked, my power suddenly surged back to its normal strength.  Amy was killing the bugs she'd fucked up, so they weren't scrambling my power anymore.  She'd realized I was trying to help.



``Should I attack?''  Sundancer asked.



``No,'' Grue almost barked the word.  ``You'll give away our location.''



``Let me,'' Trickster said.



While Trickster unclipped grenades from the belt of his costume, I focused on Amy.  She was standing, slowly, masked by a swarm.  If I sent a decoy running in one direction, I was almost positive it would get Amy killed.  She couldn't run faster than Siberian, and however much I scattered the decoys, Siberian could dispatch them all and get her hands on the real Amy in a matter of seconds.  If I moved a decoy too fast, it would be a dead giveaway as a fake.



``Really need a distraction,'' I said.



``Are you still looking for the real Siberian?''  Tattletale asked.



``Of course I am!''  I snapped.  I might have gone on to point out how we were also here to save \emph{her}.  To save Amy Dallon.  I kept my mouth shut: pointless to waste my breath or dedicate any focus to arguing when I could be trying to deal with Siberian.



Trickster was looking through his binoculars, holding one grenade.  I saw him pull the pin a second before the grenade in his hand was replaced by a fragment of building.



An explosion erupted a matter of feet from Siberian.  The smoke cleared quickly enough, and I saw her turning her head, looking for the unseen attacker.  I ducked my head low to get more cover from the ruined wall we all lurked behind.



``Grue?'' I asked.



He hesitated.



``Please.''



``Right.''  His darkness began to flow from his hands.  I climbed up onto Sirius's back, and Grue was a step behind, taking a seat in front of me.



``Any luck?'' Tattletale asked.  She'd seated herself on Bentley, her hands on the chain around his neck, and both Trickster and Sundancer were behind her.



My bugs were still searching for the real Siberian.  Or her creator, depending on how one wanted to look at it.  I was reaching the edges of my range and I hadn't found anyone suitable.  I did find two adult men that were together.  Could she have made a friend in her real identity?



Just to be safe, I set my bugs on the pair of them.  I didn't use anything deadly, but I had bugs biting and stinging without flexing their abdomens to inject the accompanying venom.  Siberian didn't react to my assault of the men.  I put each of them down as a `maybe', planting bugs in the folds of their clothes to mark them.



``Can't find her maker,'' I said.



``My power's not detecting him either,'' Grue replied, ``But my coverage is bad.  Give me a second and I'll let you know the second my darkness connects with him.''



Siberian had noticed the darkness, and I could see her contemplating coming after us, striking at the source of the darkness.  Instead, she turned and began making her way toward Amy.  The darkness continued to flow, low to the ground, tendrils rising to bind together and fill in gaps, and my view of Siberian was soon blocked.  There was another explosion as Trickster deployed another grenade, but it wouldn't serve as anything but a split-second distraction.



I could \emph{feel} Siberian.  Through my bugs, I could tell the darkness hadn't reached around that corner to where Amy, my newly reformed decoys and the two sections of truck were.



It was as good a time as any.  We needed to delay, so I wrote the words `run in 3' in front of Amy, along with an arrow.  The three transformed into a two.  Then a one.



I sent the decoys off in different directions.



Siberian lunged just as I'd expected her to, crashing through the decoy that was moving fastest.  She plunged her hands into the nearby wall and ripped out a chunk of brick and mortar, flinging it.  It broke apart as it left her hands, forming a scattershot spray.



More than one fragment of brick hit Amy, judging from the way she stumbled.  None of the hits had been too serious, at least, because she managed to keep moving.



Using my swarm-sense, I formed a mental map of the area.  Buildings, cover, features of the terrain.  What was a good option?  Should I drive her to keep running or to find cover?  Would Siberian be able to second-guess my suggestions?



She was experienced in this sort of thing, and would be an experienced tracker.  The water that layered the street was something of a blessing, I suspected.  Even as it slowed Amy down, it meant there weren't tracks of mud or anything for Siberian to follow.  At worst, there would be clouds of muck stirred up by Amy's footfalls, and there was little enough sunlight that I wasn't sure how much of it Siberian would be able to see.



I waited, tense, as Amy ran.  I felt the darkness roll over the bugs I'd gathered on and around her, and crossed my fingers that Siberian didn't have any tricks up her sleeve.



Needed a way to communicate with her.  Shifting a small group of bugs onto Amy's right hand, I felt her shake them off.  I tried again, and she left them there.  I moved them gradually, until they were gathered on the tips of her ring and pinky fingers.  She moved her hand to the right, and I shifted the bugs to her middle and index fingers.



Would she figure it out?



She moved her hand again, and I adjusted the placement of the bugs.  From the way she picked up speed, I could tell she was taking my directions.  The bugs would serve her as a compass.  She wasn't running as fast as she might, otherwise, but she seemed willing to trust that I wouldn't direct her straight into a wall.



That left the problem of Siberian and whether she would come after us when she lost Amy's trail.



``Let's go,'' I spoke.  ``Let's check the twelve o'clock position from Siberian to see if we can't find her creator further on.  Loop around.''



Grue and Tattletale kicked the dogs into action.



I judged that Amy and Siberian were far enough apart, now.  I used my bugs to direct her to a door that was ajar, leading her into a small shopping mall.



I tapped hard on Grue's shoulder, and the darkness immediately around us began to fade.  I asked, ``You can tell where Amy is?''



``I have a bit of her power.  Don't trust myself to use it,'' he grunted.  ``Missing something in the interpretation and analysis part of it.''



``Clear the darkness around her so she can find a spot to hide.''



He grunted a response, and the darkness folded around us a second time.



I was focusing on four things at once: staying seated behind Grue, guiding Amy, tracking Siberian's location and trying to find Siberian's real body.  I could sense her as she made her way up the side of a building.



Grue's darkness was heavier, now.  It sat lower on the streets.  From her vantage point, Siberian couldn't see us, couldn't see Amy, but she could see the tops of taller buildings.



What was she looking at?



Through my swarm-sense, I could feel her dropping back down to ground level.  I expected a splash or shattered pavement, but there was nothing.  She was snapping her invulnerability out to affect the surface she was landing on.



She was heading in Amy's general direction.



I reached up and pulled on Grue's right arm.  He veered in that direction.



Couldn't find Siberian's real body.  Was it really close, like Cherish had said?  I noted one man who fit the general description, but he was barricaded in his room, surrounded by cans of food.  There was no reason for Siberian's real persona to situate himself \emph{here}.  Even so, I tested him, attacking him with bugs to see if it got a response.



Not that I was sure that there was a link connecting his real self and her projected form.  It was an assumption, and maybe a dangerous one.  I wasn't sure exactly how much control Brian had managed with his own projection when he'd borrowed that fragment of Siberian's powers.



No.  My gut told me Siberian wouldn't operate like this if there wasn't some link.  There had to be some kind of range limit on the projection, or he wouldn't have any reason to follow Siberian from city to city.  The fact that he was supposedly in this area meant it might even be a fairly short range.  If he was an unwilling participant, a recipient of a power with unfortunate side effects, like Labyrinth, then she'd have to direct him from one place to another with threats.  It would require more interactions between her selves, and that would mean something would have been given away.



Along similar lines, if she depended on him to keep her going, then she had to keep him safe from the other members of the Nine.  There was infighting in the group, apparently, though I'd seen no sign of it with the team thus far.  Keeping the ordinary man safe wouldn't be a problem if he shared Siberian's senses like I shared those of my bugs.  She could keep an eye out for trouble and he could slip away or hide if a member of the Nine came around.



Until Cherish joined the group.  I wonder how that had played out.  Some sort of deal?  Threats, overt or implied?



Siberian was on the far side of the two-lane road that stood beside Amy's hideout.  She didn't walk straight for Amy, but walked down the street with an almost casual slowness.  She had one arm out, a hand tracing the side of the building she was walking by, as if to guide her through the effects Grue's lightless world.



My swarm felt dust shower onto them in her wake.  It was unexpected, and it demanded investigation.  I moved them across the wall, and felt a gap.  She wasn't just putting her hand on the wall, but her hand and forearm \emph{through }it.  What did that mean?



My bugs felt more dust fall from above.  A moth was bludgeoned by a rock that fell from above.



I felt realization hit me like a bucket of cold water.



Her hand was punching through the exterior wall of the building, but it was also tearing through the supports and load bearing areas.  She'd made her way halfway through the ground floor.  By the time she finished, part of the building was going to collapse and fall.



If the building tipped in the direction of the shattered area, it could easily fall on the mall where Amy was hiding.



My bugs formed a picture on a wall near Amy.  A rectangle to represent the skyscraper Siberian intended to bring down, a squatter rectangle to represent the mall, a ladybug for Amy and a moth to represent Siberian.  I demonstrated what was about to happen.



Faster and easier than explaining with words.



Still, I included one word for good measure:  `RUN'.



I could feel Amy making a break for it.  She headed in the wrong direction at first, northwest instead of northeast, and I used a giant arrow to direct her.



The building began to collapse only ten or fifteen seconds after I'd transmitted the message.  Grue's power didn't do anything to stop the rumble from reaching us.  From what my bugs could gather in the chaos that followed, the building seemed to slump, the lower levels buckling and crackling.  Just when I thought it had settled, the upper portion tipped over, crashing into the small parking lot and the entrance of the mall.



Amy wasn't in the impact site, and she probably wouldn't have been even if I hadn't warned her.  Still, it was a demonstration of power, it was intended to scare an already terrified Amy, and it served both purposes.  She was running directly away from the site of the devastation, ignoring the bugs I had on her hand.  In her pell-mell run , Amy stumbled into a post meant to keep carts from being taken out of the mall and fell hard.



``Right,'' I spoke into Grue's darkness.  He obeyed.



Siberian was giving chase, entering one end of the mall at the same time Amy made her way out of the opposite side.  Siberian had guessed the most likely hiding spot and then used the falling building to dash Amy's hopes of safety and get her out of hiding and running.  With the way the roads funneled together into one four-lane road, Amy would either have to take a left, take a right, or go straight.  Chances were good she would take the latter, because it put her the furthest from Siberian.



With my directions, we looped around the mall and made a beeline for Amy.  Siberian was advancing too, but while she was in the right general area, she didn't have a means of finding Amy, specifically.  Instead, she leaped from one area to another, pausing for a second or two at a time.



What was she doing?



I swept the area with my power, but I couldn't find anyone resembling Cherish's description of Siberian's real self.



Was I missing something?  If Cherish had been lying outright, I was under the impression that Lisa would have caught some tell.  There had to be something else to it.  Something I could use to identify the man behind the monster.



What was she?  Unstoppable, a deceptively strong, deceptively tough juggernaut of a woman.



Something caught her attention.  A vibration in the road?  Or had she used her power to protect the ground, and sensed some impact as the dogs walked on it?



Either way, she started to chase us.  We could have turned at a right angle, to hopefully throw her off, but both Grue and I knew that if we did, and she continued straight, she'd run straight into Amy.



\emph{Fast.  }She was fast.  Not as much as Battery or Velocity might have been on a good day, but highly mobile.



The thought clicked into the blank I was looking to fill.  How was her alter ego getting around?  I'd assumed he was traveling on foot because that was how ninety-percent of the city was getting by.  Very few cars on the road had access to gas and the ability to traverse the broken, flooded streets.  But if there was a range limit to the projection, how was he keeping up with the woman who could ignore air resistance and leap across a city block in a single bound?



I shouldn't have been looking for people.  I should have been looking for \emph{vehicles}.  Had I overlooked anything like a truck or a van interior he could be hiding inside?  Or was he still in a location outside of my range?  Or -I wasn't ignoring the possibility- had Cherish lied or misled us?



\emph{Damn it}!  The extra possibility threw my hopes of finding the man totally out of whack.



My respect for Grue grew a hundredfold as he veered straight for Amy without my asking him to.  We swept past her, and I caught her around the shoulder.  Grue offered one hand, and we lifted her together, kicking and struggling, onto my lap.  I wrapped one arm around her chest, to keep her securely in place.  She was breathing hard, almost hyperventilating.



It took her a few seconds to realize we weren't Siberian.  She might have calmed down at that realization, but she didn't get a chance.



Siberian closed the gap in a single bound, crashing into Bentley, Lisa, Trickster and Sundancer and shoving them forward into the rest of us.  We sprawled, and I felt my leg bend painfully as Sirius rolled over it.



Grue banished his darkness.  I could see the six of us and the two dogs, lying on the road. Nobody dead.



And there was Siberian.  Faintly glowing eyes, black and white striped skin, straight hair in similar variations of black and white, trailing to her tailbone.



``Thank you, Grue,'' Tattletale said.  Had she asked him to cancel out his power?  It wasn't like he was borrowing any power that would work on Siberian, and as for the concealment effects, they wouldn't do much.



And, as it turned out, she wanted to talk.  She pulled herself up to a standing position and raised one hand, palm facing Siberian.  ``Hold on.''



Siberian stopped.



``I think you should know,'' Tattletale smiled, ``We're here for three reasons.''



Siberian's eyes narrowed.



``Reason number one, we're trying to save that girl.  I mean, if I'm being perfectly honest, I don't know if I would have risked it, but we do have some more compassionate people on our team.''  She glanced at me.  ``For better or worse.''



I could see Siberian flex her fingers.  Her nails were long, and they were sharp.  There wasn't anything special about them, on an aesthetic level, but they did have the benefit of her power.  If she raked those across a surface, they \emph{would} leave gouges.  Didn't matter how hard or dense the material was.



``Reason number two, we're aiming to kill you.  See, we know about your\ldots other self.''



There wasn't the slightest reaction from Siberian.



``And the third reason, I think you should know, is sort of tied into the first.  We're making you waste time.  Longer you take to kill Panacea, here, the better off we are.  Awfully arrogant of you to leave your team and go off to pick off candidates like Amy.  The rest of your team?  Crawler, Jack, Mannequin and Bonesaw?  Right this second, they're getting a surprise visit from the rest of \emph{our} team.  What do you think-''



Siberian flickered and disappeared.  Tattletale's jaw dropped.



``\emph{Shit},'' Trickster cursed, ``She-''



``Just get a phone!  Warn them!''





