





``They're not answering,'' Tattletale reported, as she lowered the phone from her ear.  ``They're already engaged.''



``You fucking idiot.  I swear,'' Trickster stabbed one finger in her direction, ``If Ballistic dies because you fucking gave it away-''



I could see Tattletale's eyes narrow, ``My power told me there was a damn good chance she'd just run for it.  Eighty, ninety percent.''



``Well, your power was wrong, wasn't it?'' Trickster retorted.



Tattletale ignored him, looking at me, ``Anything?  Can you find him?''



I shook my head.  ``No.  I think he might be in a vehicle, so he can keep up with Siberian.  I realized it late, I haven't been looking for one this whole time, but I'm sweeping the area now.''



``Shouldn't we go?'' Sundancer asked.  ``We can go help Ballistic and your team.''



``Would love to,'' Grue said, ``But Bitch warned us about using her dogs past the fifteen minute mark.  It's wearing off, they're getting smaller and weaker, and if it gets to the point that they're not comfortable carrying the load, they may lash out.''



``How many minutes has it been?''  Trickster asked, glancing at Bentley.



``Long enough I wouldn't risk it,'' Grue said.



I looked at Sirius.  I hadn't noticed while we'd been riding him, but he \emph{was} smaller.  His exterior tissues were fitting looser, in the same way skin tended to hang loose on someone who had been morbidly obese and recently lost weight.



And just to his left, I could see Amy backing away, holding her hand.



``Amy,'' I spoke.



She startled as if I'd slapped her.  Everyone's eyes turned to her.



``You okay?''  I asked.



``No, I'm \emph{not} okay.''  Her head trembled a little as she turned to glance at the others.  She returned her attention to me.  ``She bit off my fingers.''



``I'm sorry,'' I said.  I raised my hands to show her I wasn't armed.  ``We tried to get to you as fast as we could.''



``My fingers,'' she moaned, as she looked at her hand.  ``I ran as fast as I could, but it wasn't fast enough.  She kept catching me.''



``I know.  There was nothing you could have done,'' I said.



``It's not right,'' Amy shook her head.  She was still backing away. ``This isn't the way things should be.  Superpowers and Endbringers and things like Siberian\ldots it's so fucked up.  We- there should be a way to fight back, but there isn't, so much of the time.''



``There is,'' I said.  ``It's hard to find, but there's always a way.''



Tattletale turned her head, ``Hey, Amy, listen.  Can I ask you a quest-''



``Don't,'' Amy snapped, shifting gears from self-pity to fury in a heartbeat.  ``Don't talk to me.  Don't even \emph{look at me}, you bitch.''



``This is important.''



``What part of what I just said did you not understand!?''



``You'd think we didn't just save your life,'' Trickster said, folding his arms.



``You did it to delay Siberian.  Or so\emph{ she }said,'' Amy replied, glancing at Tattletale.



``It was one of the reasons,'' Tattletale started, ``Skitter-''



``Shut up!''  The words were a screech as they came out of Amy's mouth.



Tattletale turned a hundred and eighty degrees, so her back was to Amy, and looked in the direction of Grue and I.  ``I'm done.  No point, fuck it.  I'm going to try calling the others again while you handle this.''



There were a few long seconds of tension as we all stood there, Tattletale a short distance away, phone to her ear.



I decided to break the silence.  ``How are your fingers?  You're using your power to keep the bleeding down?''



Amy glanced at her hand, and a dark look crossed her face.  ``Yeah.''



``I've got bandages, if you want them.  Only the most basic first aid supplies, but maybe they'll help?''



``Okay.''



I got the small kit from my utility compartment and approached her.  She kept still while I got out the disinfectant, bandages and tape and covered the fingers Siberian had shortened by one segment.



``How can you even be teammates with her?''  Amy asked me.  ``Are you friends?''



``We are.''



``Everything that happened to me, it's like it all snowballed out from the moment you assholes robbed the bank.''



\emph{Me too}.  I'd met and ultimately joined the Undersiders because of Tattletale, and everything had followed from that.



``She didn't plan that.  It might have started that way, but she wasn't the cause of everything that followed,'' I said.  I wondered if I was trying to convince myself.



Amy glared down at the ground.  A quick glance showed that Grue, Trickster and Sundancer were all trying to avoid engaging in this conversation.



She spoke at a low enough volume that I doubted the words were reaching the others.  ``I've had nightmares about her.  Not saying I take back how I shouted at her, but she brought up shit, and the fact that Victoria heard it, I couldn't shake it.  It affected the way I thought, the way I acted.  Victoria knew something was up, she respected my privacy, but she had suspicions.  If Tattletale hadn't said anything, I could have dealt with Bonesaw coming to my house and fucking with me, getting me to break my code.  Or Bonesaw might not have come at all.  I don't know.  Victoria would have listened to me, maybe.  Given me the benefit of the doubt.''



``We didn't expect you to be at the bank.  We were cornered, Tattletale used the power she was given to get us out of that spot.  I'm sorry it happened.''



``She was the catalyst in my whole life falling apart.  Tattletale was.''



``Maybe.''



``And you can be \emph{friends} with her, and you still think of yourself as a good person?''



``I\ldots don't know that I do think of myself that way.  I've probably done more damage than good, by trying to help others.''  \emph{Dinah, the people in my territory, now Brian.}



``But your intentions were good, then?  You were trying to help?''



``Yeah.''



``Then tell me what to do.''  She didn't meet my eyes.  ``I don't know anymore.  I've spent so long helping others, and I'm so scared, I feel numb.  My brain isn't working.  Can't think straight.  I-  I just don't know anymore.  I'm not making any promises, I won't fight, won't face the Nine, don't want to talk to Tattletale, but\ldots'' she trailed off, unable to finish her thought.



I swallowed.  I couldn't even manage with myself, and now she wanted me to guide \emph{her}?



``Okay,'' I said.  My mind was going a mile a minute.  She was one of the most powerful parahumans native to Brockton Bay.  How was I supposed to use her?



One idea crossed my mind, and I hated myself for thinking it, for the stark fear I felt at the thought.  ``Okay.  I won't ask you to face the Nine.  But you can give \emph{us} the ability to go after them, to fight them.  There's this part of the brain that Bonesaw called the\ldots Corona something.  Corona potential?  Can you access mine?  Tweak my power, give me more range?  As much as you can.''



The mental image of Bonesaw cutting through my skull with her saw was so real I could almost feel the sensation of it.



But we had to stop Siberian.



``I can't affect brains.''



``You can't-''  I sighed.  We all had our limitations and barriers.  I was simultaneously relieved and disappointed.  I didn't argue the point.  ``Fuck.  Okay.  The dogs.  Can you charge them up?  Figure out how Bitch's power is affecting them, and either make them big again or keep them from getting any smaller?''



She glanced at Sirius.  I'd gotten so used to them I'd nearly forgotten just how horrifying they were to look at.



``I'd have to touch them.''



``Yeah.  They're not as bad as they look.  They're regular dogs, it's only appearances and size.''



``Regular dogs still bite people.''



``Yeah.''



``I don't want to lose more fingers.''



``I know.  You don't have to.  Let me think.  We can come up with another way for you to contribute.''



``Can you grow us wings?'' Trickster asked, in a wry tone.



``I can't generate flesh from nothing, and it's \emph{slow} to convert something into a part your body won't reject.''



``Of course,'' Trickster said, with a note of sarcasm.



\emph{Not helping, }I thought.  Amy was willing to do something.  It was useful.  We didn't need to discourage that.



Before I could finish my thought, I saw Amy walk up to Sirius and offer him one hand to sniff.  She flinched as he moved his head, pulling her arm away.



I joined her side, and put one hand on the side of Sirius' neck, digging my fingertips into a meaty cord of muscle.  I scratched with enough force that I might have left tracks in normal skin.  ``Hey, boy.  You're a good dog, aren't you?  Yes you are.''



His bone-crusted tail lashed behind him in something approximating a wag.



Amy put out her hand again, and Sirius sniffed it.  Gingerly, she laid her hand on the length of his snout, running her fingers over calcified muscle, bone spurs and braided lengths of muscle and other tissue.



``The hell?'' she muttered.  ``Can't wrap my head around this.''



``You can't make him bigger?''



``No, I don't think I can.  Can't make something from nothing.  But I think I can stall the shrinking.  Whatever I do might get undone the second he's back in range of Hell- of Bitch.  It's hard to describe.  I can see the aftermath of what she does, but not the process.  It's like the tissue grows, then it dies as it gets pushed out of the core, but some of it stays functional\ldots there's a normal dog inside there?  Intact?''



``Yeah.''



``Okay.  Think I've got it.  He's not going to shrink anytime soon.''



I signaled Tattletale to return.  ``Thank you.''



She walked over to Bentley, giving Trickster a wary look as she walked by him.  I joined her, in part to give Bentley the reassurance that this angry stranger wasn't so dangerous.



``There,'' Amy said.  ``You're going to save your friends?''



``And if we can, we're going to put down the Nine.  We figured out Siberian's weakness.''



Her eyes widened slightly at that.  ``What?''



``What did you think we meant when we were talking about her other self?''



``A secret identity?  I- I wasn't really paying attention.''



Tattletale climbed up onto Bentley's back, studiously ignoring Amy.



``Kind of a secret identity.  She's a projection,'' I said.  ``Like Crusader has with his duplicates.  Best case scenario, we can find her real body and put her down.''



``Just like that?  You'll kill her?''



``Ideal world,'' I said.  Grue had climbed up onto Sirius's back, and he offered me a hand up.  ``Won't know if we're capable until it happens, but I'd like to think we have the courage.''



``But you're risking your lives.''



``Yeah.''  I got settled and wrapped my arms around Grue's body.  He didn't react or protest.  My head just inches from his back, I turned to look down at Amy, ``See, it helps that we're \emph{pissed}.''



``I'm pissed too,'' Amy said.



I offered my hand to her, in case she wanted to climb up behind me and join us, but she stepped away.



``But you're more scared than pissed,'' I said.  She looked away.



``We should get going,'' Trickster said, as Sundancer got in position behind him.  We were all seated and ready to head to the rescue.



``One second,'' I told him.  ``Amy.  Listen.  It's okay.  I've thought of another way you can help, and it doesn't put you in any danger.''



``What is it?''  She still didn't meet my eyes.



``You're going to cut loose with your power.  I can feed you the raw materials, you do what you can.  You know how my power works?''



``Pretty much.''



``Send the bugs my way when you're done with them, then.''



``You're a villain, you know.  You're asking me to betray the family I grew up with if I'm helping you.''



I stared at her.  We were so similar in such different ways, but I couldn't even begin to comprehend her train of thought.



Why were the people who clung so fiercely to the notions of right and wrong the very same individuals that had the worst grasp of what they meant?



Maybe I wasn't one to talk.



``I don't think you're one to talk about betraying family,'' Tattletale spoke.



I could see all the color drain out of Amy's face.



``Hey, Tattle,'' I started.



``No.  Sorry, Skitter, but it's my turn to talk now.  We're short on time, and we \emph{really} should leave now, but if we leave it like this, you're going to be distracted.''



I shut my mouth.



``Amy?  I know what you did.''



``Don't you dare-'' Amy started.



``You fucked up.  You crossed one of the lines that's reserved for the real monsters.  You know it, I know it.''



Amy's face crumpled.  I didn't have a better way of describing it, the way her expression twisted, going from plain to almost inhuman from emotion alone.



I almost spoke up.  I wasn't sure why I didn't.



``You think you're the lowest of the low, that you're scum.  You despise yourself.''



Amy couldn't even mount a response.



``You're wrong.  You're not there.  Not \emph{yet}.''



Amy looked up at Tattletale, wide-eyed.  The look was utterly defenseless.  I was put in mind, for just an instant, of just who Tattletale \emph{could} have been.  I had a mental image of her as a cult leader, tearing people down with an almost surgical precision, then molding them into who she wanted them to be when they were emotionally and mentally unable to mount a defense.



``Not yet?'' Amy asked.



``Not yet.  You shouldn't hate yourself for what you did in a moment of desperation.  Hate yourself for what you do after.  Hate yourself for your cowardice, your refusal to step up and help at this moment, right now, your refusal to participate in this world that you never even tried to understand.  That's a conscious call you're making, and you \emph{know} it's the wrong one.''



Amy hugged her arms to her chest.  She shook her head a little, as if she was denying what Tattletale was saying.



Tattletale went on.  ``You need to make the right calls, and you need to start now, because you're approaching the point of no return.  You start making amends, you start doing your part, and you undo what you did, and you do it ASAP, because if you don't, you're going to hit the hard ground at the bottom of that slippery slope.''



``But-''



Tattletale didn't give Amy a chance to finish.  She kicked her heels and Bentley charged off.



Grue moved to follow, and I turned to Amy, ``If I send my bugs to you, will you-''



``I'll-  I'll come.''



I blinked.



She stuck her hand in my direction, and I caught it, helping her up to a seat behind me.  Sirius shook slightly, as if he could shake us off.  Were we too heavy?



Apparently not.  He bolted after Bentley, and we were off, Amy clinging to me like her life depended on it.  I suspected that had little to do with the fact that we were riding on one of Bitch's dogs.



The clawed feet of the dogs pounded pavement as we made our way towards central downtown.



I could feel the sensation of Amy doing something to interfere with my powers.  It began to get worse, reaching a peak, and then getting \emph{worse}.  Just when it had reached the point where I was going to tear her hands from around me and let her fall off Sirius's back, it began to clear up.



I could feel the bugs, but they weren't anything like what I'd seen in Brockton Bay.  Superficially like dragonflies, with fatter bodies.  I couldn't grasp every process in their body, making them feel strangely hollow and artificial.  What I \emph{could} feel was a kind of echo in my power.  It made control harder.



She had to have a reason for doing what she was doing.  I tried directing them to move, and they took off.  No problem on that front.



I couldn't ask what she'd done, because we were moving fast enough that the wind in our ears would drown out my voice, and the run was jarring enough that I worried I would bite my tongue if I tried talking.



Instead, I experimented.  I tried operating their bodies, engaged in the usual practices for injecting venom, nothing.  They weren't weaponized, I was almost sure.  I even placed some aphids on them to get a feel for their exteriors.



It was only when I moved them out to either side of me that it dawned on me what the echo was.  Experimenting, I sent them to the limits of my range to confirm my suspicions.



Whatever signal my power sent to my bugs, these bugs were there to intercept it and transmit it to their immediate area.  Each extended my range by three hundred or so feet around them.



Letting go of Grue with one hand, I patted Amy's hand and then reached back to give her a thumbs up.  I set more dragonflies and other various bugs down on the backs of her hand.



In another minute, I had four more relay bugs.  I paired them up and sent them forward, so one relay could transmit to the next.  Two extra city blocks of range.  I started gathering a swarm with the bugs in question.



Amy had balked at the idea of outfitting me with altered bugs.  Had she maybe settled on these, because she thought they wouldn't give me as much offensive potential?



I had them in place for less than ten seconds before I found a moving vehicle.  It was a truck with plastic sheeting over the windows, four-wheeled, with a compact rear.  A small moving truck?  It was moving faster than was safe, veering wildly as it to get through the water and over the damaged streets, and it was heading straight for central downtown.  Straight for the others.



``Found him!''  I hollered, at the top of my lungs.  Tattletale looked over at me, and I signaled, extending my arm to the ten o'clock position.



I felt strangely calm as I shifted my focus to the attack.



If it came down to it, I'd have to kill the man.



My bugs clustered on the `windshield' of flapping plastic, gathering in heavy numbers.  The faster moving dragonflies and hornets began to pelt the plastic, attempting to drive themselves through it.  Most died in the process.



He swerved sharply to try to throw the bugs off, but there wasn't enough in the way of momentum or wind.  My other flying insects began to ferry larger black carpenter ants onto the windscreen, to use their sharp bites to penetrate the plastic sheeting.  We were making holes, but the attempts of my swarm to worm their way through the holes and open them enough for the more dangerous bugs to get inside were stymied by the wind and the flapping of the plastic.  Every movement, however small, threw off my ability to track where the existing holes were.



We had a bead on him, and the dogs were better suited for rough terrain than the moving vehicle.  It was only a minute before we caught up.  As I'd guessed, a white moving van with a giant icon of a hand on the back with the words `Haul It!'



I might have found it amusing if the circumstances were slightly different.



He noticed us shortly after we noticed him.  Siberian flickered into existence on top of the vehicle, standing, her legs shifting to adjust her balance as it hit a crack in the pavement and rocked slightly to one side.  I heard Amy shriek as she saw Siberian.



Tattletale veered left, hard, and Grue turned us right.  We each cut into side streets, running parallel with the truck.  Bentley was lagging slightly behind, but I caught a glimpse of the other group as we made our way past a major intersection.  Two blocks away, slightly behind us.



I heard an explosion, and Amy clutched me tighter in reaction.  Glancing down, I could see her arms around my ribcage, the hand with the maimed fingers held slightly off and away so it wouldn't get bumped or jostled.



Trickster was handling the opening salvo.  The objects he was swapping for grenades weren't even close in size -signs and traffic cones- so the timing was horribly off.  Siberian didn't move from her perch.



Grue steered Sirius into a sharp left, and the dog's claws skidded for a grip on the flooded street before we turned.  We got one block and then turned right, putting us directly behind them.



I could see Siberian tense, as if intending to jump, but another explosion from Trickster kept her in place.  She was protecting the truck, surrounding it with her forcefield.  I wasn't sure how it was able to interact with the road, but a grenade going off under the front of the truck failed to achieve anything.



There would be nothing to stop her from staying there until the truck reached
the other Nine.  It would out Siberian's real nature to any of the Nine who didn't know, and that wasn't a total loss, but it also meant our teammates would be blindsided by her arrival.



I felt something bump my hands.  Grue was holding the chains that led to Sirius's muzzle.  He bumped my hands agan, and I took hold of them.



With his own hands free, leaning hard against me for support, he reached out and buried Siberian and the truck in a carpet of darkness.  Following, we soon plunged into the wake.



The second we were out of sight, I shifted our position so we were running in the left hand lane, rather than the center of the road.  Didn't want Siberian guessing our position and pouncing on us.



I could sense the surroundings with my bugs, but my power was diminished.  I was aware of Grue, Amy and Bentley, of Tattletale, Trickster and Sundancer a short distance away, keeping pace.  I could see Siberian and the truck.



I couldn't detect any sign that Grue was projecting anything with Siberian's power.  Whatever she was doing to the truck, it was protecting her from him.



The upside was that the driver was blind.



I could tell because he drifted.  It was gradual at best, but he veered slightly to the left.  With no point of reference, he didn't know he needed to correct.  A moment later, he smashed into the face of a tall building.  Siberian's power meant the truck took no damage, and the driver corrected course, but soon enough, he began to veer again.



This wasn't getting us anywhere, and we were running the risk that he'd hit someone, crash into or through an inhabited area.



Through my swarm, I could feel Tattletale waving.  Grue hadn't swamped her in darkness, so there was nothing hampering her progress.  What did she want?



More to the point, how the hell were we supposed to communicate?  I reached a block ahead of her and formed my bugs into a word.  `WHAT?'



She tapped her hand to her eye, then to the top of her head.



Again, I formed my bugs into a word.  `WHAT?'



She tapped her head a few more times.



I was disappointed that a girl with superpowered intuition couldn't come up with a better signal.  What did she want?  Eyes could mean see, head could be about thinking?  Her power?



She reached back over Trickster's shoulder with one hand while holding the reins with the other.  My bugs had to settle on her finger to follow her gesture.  Pointing?  She was pointing behind him.  At Sundancer.



Eyes, brain, Sundancer.



She wanted to see, to use her power, to use Sundancer?



Tattletale was waving now.  The opposite of a beckoning gesture.  A scooping motion, as if to push us away.



She wanted us to go away?  To get back?  She wanted to deploy Sundancer's power.  That made sense.  And she wanted to be sure we were out of the line of fire?  She could only do that if she saw us, and she could only use her power if she could follow what was going on.



From my seat behind Grue, I steered Sirius around another corner, then brought us up behind Tattletale's group.  We gradually caught up.



``Do it!''  I shouted as we began to pull alongside them.  Siberian would be out of range of Grue's darkness in moments if Grue wasn't behind her, replenishing and extending his power.



``Where is she!?''  Tattletale shouted.  Sundancer was leaning back, her hand out to one side.  The orb she was creating was small.



I pointed.



The orb was getting larger.  The size of a baseball, a beachball, an armchair.  As it grew, it drifted farther away, higher.



By the time it was directly overhead, it was large enough to swallow up my bedroom whole.



``Gotta stop them!''  Tattletale called out, ``We blindside them!''



``Civilians!?''  Sundancer cried out.



``Some!''



``Let me know-''  She grunted as Bentley stumbled over a pothole.  ``Let-''



``Got it!''  I replied.



I tracked the people in nearby buildings, and kept my arm extended to point at Siberian.



``Got to use my power again!''  Grue shouted.



``Signal us!''  Tattletale called out.



We pulled right, plunging into the darkness.  It was thinning out, and faint shafts of light were piercing through.We crossed the road behind Siberian, and Grue blasted them with darkness, replenishing the effect.  We continued across the street, moving behind cover.



Only a few people in the upcoming area.  We had to be close to Regent's group.  Time was short.



I drew images with my bugs to point her in the right direction, and then formed the word with my bugs as the other group continued forward.  `NOW'.



We passed out of the darkness just in time for me to catch sight of the orb.  It was larger now.  Large enough that when it fell, it had to be touching both of the sidewalks on the four lane road.  Even with a building between us and the impact zone, I could feel the wave of heated air, and I saw the billowing steam.  Grue took the reins and guided Sirius away before it could reach us.



Sundancer hadn't hit Siberian.  She'd dropped the orb straight into the road a hundred feet ahead of them, and she'd plunged it down, hard.



My bugs died as Siberian approached the impact site, burned up by the heated air.  I could imagine what had happened.  The miniature sun would have burned a hole into the ground, melted or even vaporized pavement.



Affected by Siberian's power or not, they were still affected by gravity.



I couldn't say what would have happened in the long run.  Had they hit the wall or floor of the pit and used Siberian's power to make it as invulnerable as they were?  Or had they plunged through it, burying themselves some distance underground.



A nearby building was burning.  I saw Sundancer forming another orb near the site, I wasn't sure what she was doing, but the flames on the building were shrinking and dying out.



This wasn't a victory.  It was a stall.  We couldn't \emph{stop} Siberian so long as she was able to grant invulnerability to her other self, but we \emph{could} keep her from reaching her teammates in any meaningful amount of time.



It was interesting, I had to note, that she was affecting the truck and not her maker.



A limitation?  A drawback?  Could she not use her power on her real body?



Clouds of white steam intermingled with the black tendrils of Grue's darkness.  We stopped running, but we didn't approach.  I focused my power on the bugs in the ground.  Ants, earthworms.  Was she tunneling?  No.  As far as I could tell, the ground was intact.  She wasn't moving.



``What did you do?''  Amy whispered from behind me.



I didn't have the breath to explain.



``Drop the darkness?''  I asked.



Grue nodded.  The darkness cleared, but the steam didn't make it any easier to see.  I saw the shadowy silhouette of Tattletale, a distance away.  I practically had to peel Amy off of me to get to my cell phone.



``Tattletale?'' I asked, the second she picked up.



``She's still down there.''  Tattletale replied.



``Why?  Hurt?''



``Don't know.  Planning her next move?  Don't get the impression she's tunneling.''



``My bugs don't either.  Hey, I'm wondering if Siberian can affect her real self?  Why doesn't she just grab him and run?''



``Good question.  But that's not our real concern.''



``What is?''



``Them.''



It took three or four seconds before I saw them arrive, stepping through the mist to stop a distance from the hole.  Identical costumes, all-concealing, with gas mask filters on the front and tinted panes for the upper faces.  Each was color coded.  Four flew, one using a jetpack.  One was on the ground, a style of super-speed I recognized as Battery's.  Rounding out their group was the ghostly image of a bear.  Ursa something, from Legend's squad.  She had three forms, or she duplicated herself into three states, or something.  I wasn't sure about the naming convention.  One for the big bear, one for the small, and one for the woman.



``Legend, Battery, Cache,'' Tattletale rattled off names through the phone, ``Chariot, Glory Girl.''



Amy squeaked, barely audible, a failed attempt to speak.



The flying man in the lead pointed his hand towards Tattletale.  If that was Legend, one laser blast could take all of them out.  I wasn't sure if he'd spotted us through the mist and smoke.



``Want me to use my power?'' Grue asked.



``No,'' Tattletale's voice came from my phone.  ``Skitter?  Inform them.''



I drew words out with the flying insects, big and bold, with an arrow pointing down at the crater.  `SIBERIAN + HER CREATOR'



Legend snapped his head from the words to us.



``\emph{Shit},'' Tattletale said.  No sooner was the word out of her mouth than Siberian came tearing out of the hole, truck held over her head.  A section of the street was torn free and flipped through the air.  Legend blasted it out of existence with an indigo flash of light.



``Cash!''  Legend bellowed the word.  He began pelting Siberian with lasers.  Beams capable of leveling buildings, and she ignored them.



\emph{Cash}?  I saw the man in the black costume raising his hands.  Dark lines began to surround Siberian and the truck, forming complex geometric angles.



In the blink of an eye, as Siberian reached the peak of her leap, panes of glossy black material snapped into place between the dark lines.  The resulting geometry contracted as if he meant to squish Siberian.  It shattered instead.



She hit the ground in a crouch, holding the truck in one hand, and the man in the black robe staggered, blood gushing from his nose.  Legend caught him before he could collapse.



\emph{Cache.}  Right.  I was dimly aware of him, though I'd never seen his picture.



Siberian charged the heroes, and they cleared out of the way in an instant.  The one in power armor -Chariot- slid across the ground with the aid of his jetpack and built-in roller skates. Legend and the one in red, Glory Girl by process of elimination, took flight.  Ursa whatever leaped to one side.  They were the mobile group, the group that was able to get here fastest.  They'd seen the sun appear, they'd seen it hit, and they'd come to step in.



Siberian didn't stop to engage the enemy.  She continued on her course, charging through the ground floor of a building as she swung the truck in a lazy back and forth arc.  I could see the roof buckling as vital supports disappeared.



Legend handed Cache to Ursa and gave chase.  I could see Chariot raising his hand to his right ear, pausing.



He, Battery and Glory Girl turned and advanced towards Tattletale's group.



``Can we go?''  Amy asked, from behind me.  ``I didn't- I didn't think-''



There was a pause.  We \emph{could} fight.  My power would be largely foiled by those suits, but Grue had his power.



``No,'' Tattletale said.  ``Come here, and bring Amy.  They want to talk.''



Amy pulled back, and I grabbed her wrist.  Before she could hop off Sirius, Grue was directing the dog across the road.



Chariot and Glory Girl pulled off their helmets as we arrived.  Chariot was black, his narrow, triangular face largely covered in power armor.  He had the scruff of a weak teenage beard on his chin.



Glory Girl bore little resemblance to any of the last times I'd seen her.  There were dark circles under her eyes.  She stared at me.  No- at Amy.  The glare seethed with raw, seething hatred.  It made every line of her face hard.



``You've joined them, now?''  She spoke, breaking the brief silence.



``I just wanted to help against the Nine,'' Amy said.  Her voice was small, defeated.  ``Can I-''



``If you open your mouth and ask if you can use your power on me, I won't be held responsible for what I do,'' Glory Girl growled.



``Don't hate me, please.  I don't care what you think of me, but hate is too close to\ldots''  Amy trailed off.



``Too close to what?'' Glory Girl asked.  She shrugged.  Anger gave an edge to her words.  ``Aren't you going to say it?  Can't you admit what you did?''



Amy hung her head, and her forehead rested between my shoulders, hair hanging down.  She shook her head, but I doubted Glory Girl could see it.



``Let's put vendettas aside,'' Chariot spoke.  He smirked.  ``We have bigger fish to fry.''



``The Nine,'' Trickster spoke.



``The Nine,'' Chariot said.  ``But it's not my place to talk tactics.  I'm just the rookie.  The messenger.''



He extended one hand toward Tattletale.  There was an earbud in his palm.



``The Director of the PRT would like to have a word with you.''





