





``Me?''  Tattletale quirked an eyebrow.



``Sure,'' Chariot said.  Just behind and to one side of him, Glory Girl was glaring at Tattletale.  She looked like she was ready to hit people.  It was the kind of latent hostility I was used to seeing in Bitch.



``Not terribly fair to my teammates, if it's just a one-on-one conversation.''



``Are you going to take this or not?'' Chariot asked, his hand still extended in her direction.



``No real point,'' Tattletale shrugged.  She tucked her hair behind her ear and turned her head.  ``Already have one.''



Battery stepped forward, glancing over at our team, ``This one is already set to the encrypted channel, it's faster if--''



Tattletale interrupted, ``Uplink three-three-five, encryption forty-two mod three-four-two-one-zero-zero-six-six-three-one-zero--''



``You have access to our channel,'' Battery growled, interrupting Tattletale's spiel of numbers.



Tattletale shrugged.  ``Have for a while now.''



Battery raised one hand to her ear.



``Yeah, Battery,'' Tattletale grinned, ``Let's do as the Director says and get down to business.''



Battery drew a phone from her belt and tapped her fingers on the keypad for a moment.  She gave Tattletale a dark look as she held the phone out.



A woman's voice said, ``Not like you to tip your hand, Tattletale.''



``Director.  Are we really going to pretend you didn't know I was listening in?  You've been putting out misleading details to screw with my information gathering.  Done quite a good job of it, if I may say so myself.  Very subtle, all of it just right enough that even \emph{I} was thrown off.  Couldn't trust much of it.''



``Thank you.''



``And you did catch me off guard here.  I didn't expect you to contact me.''



``You've been busy, your groups.  Fighting Burnscar in the Docks, I gather that didn't go so well,'' the Director said, pausing.



I didn't even want to think about that.  I hadn't been back to check on my people or my territory since then.  We \emph{had} been busy.



``Then you ambush the Nine, capturing two, one of whom you enslaved, but you lose one of your own in the process.  You mount a rescue attempt.  I take it that you were successful?''



``Grue's here,'' Battery informed her.  ``But he looks different.''



``So they were successful.  And now we find the Undersiders mounting a pincer attack, with this group targeting Siberian?  I suspect you're crossing the threshold of fearlessness and entering into foolishness.''



That last comment nettled me.  I spoke up, ``The Nine don't really leave you alone once you've scored a win.  We had to seize our advantage.''



``I see.''



``And she has a weakness.  Siberian, I mean,'' Tattletale said.



``Do tell?''



``She's a projection.  Like Genesis is, as I'm sure you're aware.  Like Crusader's duplicates.  A quirk in reality that draws from her creator's brain to create a body complete with all the physiological substructure.  Which is largely for aesthetic effect, and I'd guess it gives her real self something the brain is familiar with controlling anyways.''



``And the controller is vulnerable?''  There was a note of interest in the Director's voice.



``Particularly vulnerable.  She can't extend her invincibility over her real body.''



``I'm not sure I believe this.  The Nine would have discovered this and I doubt the baser members could resist taking advantage of such a weakness.''



``The power has range.  I suspect the creator can stay miles away and still manage some control, but ventures closer for voyeuristic purposes or because it offers more control and faster response times.''



``Much like Regent, hmm?''



Tattletale paused.  ``So you know that.''



From the tone of the conversation, I would have expected a `\emph{No, you just told me.}`, but Tattletale wouldn't have done that.  More likely that her power confirmed her thoughts.



Piggot nodded.  ``Shadow Stalker debriefed us.  What do we know about this woman who controls--''



``Man.  The person who projects Siberian is male.  But he creates a female body.  I think it's tied into his trigger event.  Someone he lost.  If I had to guess, he sought revenge for her, but something happened.  A side effect of the power, or just a seriously unhinged mental state\ldots he lost it.''



``I see.  Thank you for the information.  Unfortunately none of those possibilities are narrow enough that we can use them to track him down.''



``Not in the short-term.  In the long-term--''



``I don't intend for there to be a long-term, Tattletale.  This ends today.''



Tattletale paused.  ``What did you do?''



``Hmm?''



``You're planning something.  Something you're wanting to keep a secret, and it's big.''



``Tattletale, you've been observing and gathering information on the PRT for some time now.  Do you think I'm a stupid woman?''



``\emph{Stupid}?  No.  Genius?  No.''



There was the sound of a dry laugh from the other end of the phone.  ``No, I admit that's true.  But I'd like to think I'm resourceful.  I'm fighting in a ring where my opponents are bigger, stronger, smarter, faster and better equipped than I am, and the cost of failure on my end is far greater than it is for any of you.  You understand?  I'm competent, and I wouldn't waste my time trying to pull the wool over your eyes.''



``So?''



``No secrets.  I'd planned to bait you here with the same subtle offers of information you praised me for earlier, but you're here anyways, so I'll \emph{tell you} what I'm planning.  In a matter of minutes, we firebomb the area where the main group of the Nine are situated.''



``That's insane,'' I spoke.



``Was that Skitter?''



``Yeah,'' Battery replied.



``It's necessary, Skitter,'' the Director told me.



``It's breaking the rules between capes.  The same rules that hold things together in an Endbringer event.  We're fighting a common enemy.''



``True, but not the full story.  We made no agreement of cooperation, and so there can be no betrayal here.''



``My teammates are there, fighting the Nine, and they're doing it for this city.  You'd be punishing them for that.''



``Legend did warn them that they shouldn't.  He was told to, I quote, `suck shit'.''



\emph{That would be Bitch}.  \emph{Or maybe Imp}.  \emph{Probably Bitch.}



Tattletale quirked an eyebrow, ``Did he specifically tell them they shouldn't because you're bombing the neighborhood?''



``Would you believe me if I said he didn't get the chance?''



``I'd say fifty percent of it is that he didn't get the chance, and fifty percent is that he didn't try that hard.''



The Director offered a noncommittal `mm hmm' in reply.



``And you're telling us this because?''



``Because we've studied you.  We know what you prioritize, and I believe that you'll enter the fray to save your teammates.''



``Or we could phone them.''



``Do you want to try?''



Tattletale glanced at me and Grue.  ``No point, I guess.  You're blocking unofficial communications in the area.''



``Yes.  We have to hamper communication between the Nine if we want to catch them off guard.  You understand.''



``I do, and that's \emph{totally} the entire reason you're doing that,'' Tattletale said.  She glanced over in the direction of the fighting.  ``How long before the area is bombed?''



``Can't say.  On the record, as with your teammates, we're forbidding you from entering the area, but I expect you're doing so anyways.  Against my recommendation.''



``Absolved of blame,'' Grue spoke.  His voice was tight, his body tense.



The Director ignored him.  ``The moment I heard you were in the picture, I told my subordinates to change the time.  They'll inform me about the new time of attack as soon as I've hung up.  It's not a perfect solution, but perhaps your actions from this point will reveal something about your power and its limitations.  But please understand that we just can't risk that you'll inform the Slaughterhouse Nine about the scheduled attack.''



``And there's a chance we'll be collateral damage, out of the picture and out of your hair after the Nine are gone.''



``How sad, that you see monsters where none exist.''



``Right.''



``It was nice to finally talk with you, Tattletale.  You should go help your teammates, if you're going to.''



``Fuck you, Piggot.''



There was no response, and Battery deemed the conversation over, putting away the phone.



In the brief period of silence that followed, while we got ourselves ready, a voice broke through, ``Victoria--''



``Don't,'' Glory Girl snapped.  ``I didn't tell anyone what you did, but that's the last nice thing I'm going to do for you, understand?  We're not teammates.  We're not sisters.  We're not friends.''



``I'm sorry, Amy,'' Tattletale said, ``But we've got to go.''



We were moving a minute later, leaving the squad of heroes behind.  Looking over my shoulder, I could see them getting in formation, clustering around Cache, who was regaining consciousness.  Only Glory Girl stood apart, her arms folded.



Wasn't quite sure about the story there, but I was getting a sense of it.



I could feel Amy tapping my arm.



``What?'' I had to raise my voice to be heard.



``Drop me off,'' she spoke into my ear.



It took a few seconds to get the message to Grue and come to a complete stop.  Tattletale stopped Bentley a hundred feet ahead.  Trickster and Sundancer looked back with mild curiosity.  Their costumes didn't reveal much about their expressions.



``Not thinking straight,'' Amy said, ``Not enough to go into a situation like this.  Don't want to get bombed.  Um.''



``It's fine,'' I said.  ``Still willing to help?''



She nodded.



``I'm going to send you the bugs I can't use.  If you want to make more bugs that can relay my signal, that'd be great.  If you can think of something else\ldots I need firepower.''



``And we're going to be short on mobility if we need to make a run for it,'' Grue said.  ``Too many of us for two dogs that can carry people, unless we're lucky and Genesis picked a form that works.''



We'd sent Regent's group out with Shatterbird, Imp and Ballistic, with the idea that Genesis would meet them there.  They'd taken one of Coil's trucks, since Bastard wasn't old enough, big enough or trained enough to carry a rider.



``What am I supposed to make?''



``Figure it out, Amy.  If you can't think of anything, the relay bugs are excellent.  Really.''



``Okay.''  She let me help her down.



``Skitter,''  Tattletale called out, ``We should be close enough.  Want to pass them a message?''



I nodded.  I had six of the relay bugs, and it took only a minute to set them up so they formed a chain, extending my reach for an additional six city blocks in one direction.  Eight and a half in total.



I swept them outward, and the one at the furthest point lagged behind.  Still, it gave me the opportunity to cover a wide area.  Bugs mobilized throughout, and I began funneling the less offensive ones back toward Amy.  No-see-ums, earthworms, caterpillars and roughly half of the houseflies in the area began filtering back.  I maintained some of the dragonflies and other mobile bugs for the sake of getting a feel for the area.



I could sense Regent's group, running to cover.  Ballistic was bombarding Crawler, relying on the impacts to drive the brute back.  Crawler was fast -and he was agile, with preternatural reflexes- but Ballistic was unloading on him with projectiles that moved faster than sound.  Crawler dodged only two in three, and Ballistic followed up on any successful hits with a series of shots to pound Crawler into the nearest available surface and pin him there.  Genesis had formed a body that was winged.  It resembled a pterodactyl with arms, a griffon or something in that vein.  She was making an effort to drop large chunks of rubble onto Crawler.  He was strong enough that it barely slowed him down, but time he spent hauling a section of wall off of himself was time for Ballistic to get his hands on material for another shot.  Shatterbird offered support with a constant hail of glass to harry Crawler and keep him from finding traction on the pavement.



Jack, Bonesaw, Mannequin\ldots I found the former two in a parking lot.  My bugs sensed what I judged were Bonesaw's mechanical spiders, tearing cars apart and converting the components into more spiders.  There was a group of people with her, shuffling behind them.



Mannequin was MIA.  That was bothersome.  He was able to detect and avoid my bugs, which meant he was a factor I had to keep in the back of my mind.



``Found them, except for Mannequin.  Amy?  Be careful.  I don't know if Jack's team is going to break the rules they set, but Mannequin could come after you.''



I was so used to dealing with my teammates, people who were experienced in this sort of thing, that I hadn't expected much more than confirmation.  She looked legitimately scared at the prospect.



``Here,'' I directed a ladybug into my palm and extended it towards her.  ``Crush it, and I'll come.  Or transmit some signal with my power.  You have my backup, understand?''



``Okay.''  She took it, but she didn't look reassured.  The first bugs were flowing into her cupped hands.  I could feel nervous systems intermingling, two bugs becoming one, and that strange hollowness that told me I didn't have a complete grasp on how they functioned, that there was a part of them that was beyond the reach of my power.



I drew out words with my bugs, on a surface of wall where Regent would be able to see.  `Evacuate.'



He ran his fingers through the bugs.  After a moment's thought, I gathered them into a square, organized by rank and file.  It took me two tries, but I managed to make them move to form letters, then regroup.



He dragged his fingertip through the bugs to spell out a reply.  `Can't.  We run we can't keep crawler down'.



`We're coming,' I wrote to him.



``Let's go!''  I called out.  Tattletale turned in her seat and kicked Bentley to get him going.  Grue did the same for Sirius.



Having gathered as many bugs as I could, I drew my relay bugs back and spaced them around the perimeter of my own range, effectively extending it by a block in every direction.



``Have to stall Crawler long enough to make a run for it!''  I shouted.



``Have to do it in the next eight minutes!''  Tattletale called out.  Grue was getting Sirius to keep pace with Bentley, who was brawnier and slower.



``Bomb hits then?''



``Sometime after then.  Could be eight minutes and ten seconds, could be fifteen minutes!''



I swore under my breath.  Eight minutes made for a deceptively small amount of time.



The heroes were gathered.  I couldn't set them apart.  With few exceptions, they each wore an identical costume with full body coverage.  There were subtle differences in height  and body shape, which let me identify the people at the extreme ends of the physical spectrum: Vista, who was the smallest, and Triumph, the most musclebound.  Weld wasn't in the concealing costume, presumably to retain more of his shapeshifting capability.



Vista, Clockblocker, Weld, Flechette, Triumph, Miss Militia, Assault\ldots Glory Girl, Battery, Cache and the ghostly bear were joining them.  That left two more I couldn't place.  They moved in formation.



Might as well do what I could to help.  I drew out arrows and words on the ground, with names by each arrow to point them to Jack, Bonesaw and Crawler.  With the arrow length, I tried to indicate how far the distance was to each of the enemies in question.



They spent about ten seconds discussing it, then broke into a run, going for Jack and Bonesaw.  Good.



We reached the scene of the ongoing fight with Crawler.  Sundancer was off the dog and on the ground the second we could see him, creating her orb and increasing its size.  She was fireproof, but she didn't have the ability to grant that benefit to others.  Once she was standing, the orb was free to grow.



There wasn't much my bugs could do.  They settled on Crawler and found his flesh impenetrable.  I began preparing web nets, drawing lines of silk between my airborne bugs.  Amy's relay bugs had afforded me the chance to pick up far more bugs than I otherwise might have.  My attention flickered over my swarm.



Nearly a million spiders.  They were only a relatively small percentage of the swarm itself.  I had more ants, termites, flies, aphids, gnats and beetles to form the bulk of my army.



I sent the more useless ones toward Amy.  Not so many that I overwhelmed her, but enough that she always had more at hand.



\emph{He's big, he's strong, he's ridiculously tough, but he's no Leviathan.}



My spiders began weaving their threads into braids, the flying bugs directing them in and through loops of silk as the threads spooled out.  Where bugs couldn't hover, they directed their flight into tight corkscrews to slow themselves.



I wondered if this was the most bugs I'd ever controlled.  The buzz of my power thrummed through me to the point that I was barely aware of myself and where I was standing.  It wasn't just the number of  bugs, but the number of instructions.  Spiders were spooling thread, organizing by the amounts they had remaining.  Flying bugs were gathering in formations, carrying the slower bugs forward and maneuvering the spiders to spin webs.  Smaller bugs, the useless ones, I directed to Amy and formed into dozens of decoys.  Millions of instructions a second.



Estimates said that insects outnumbered people by two hundred million to one in worldwide population.  Part of that distribution was biased toward rainforests and other areas humans left uninhabited.



At the end of the day, that was just insects, and there were more creatures under my sway than the six-legged variety.  I could feel them in the earth, in the walls, beneath the pavement, even.  Even from the weeks after I'd left the hospital, I'd dismissed them as background noise, just sources to draw from in amassing my swarms.



Now, it felt different.  My range was extended, and it wasn't because I was distracted, cornered, trapped.  As Crawler noticed us and shifted his position to keep us all in line of sight with his innumerable eyes, I had a few moments to think, to experience my power at its best.



We were so small.  Even in the scope of a single neighborhood, my power extending for roughly a thousand feet in every direction, it made us all seem tiny.  Even Crawler.



``Don't use your orb on him,'' Tattletale cautioned.  ``Won't do us any favors, and it'll only make him stronger for the future.''



``Then what should I do?''



``There's no civilians here.  Legend and the others have evacuated.''  I told her.  ``The buildings are empty.



She nodded, apparently grasping my meaning.



``You go high, `Dancer, I go low?'' Grue asked.



She nodded.



I held back as they advanced, ready to make their move.  Ballistic caught Crawler with a projectile, and the monster went sliding.  Shatterbird hit him with a wave of glass to keep him down, and Genesis swooped down to smash him over the head with the wreckage of a small car.



It did surprisingly little to keep him down.



Grue and Sundancer made their moves, Grue swamping Crawler in darkness while Sundancer brought her orb around into the face of the building.  With her miniature sun, she sheared through the concrete and metal, zig-zagging the orb through one floor.



The supports obliterated or melted, the building crashed down to the street with enough force that the rolling cloud of dust and was enough to drive us back.



He had to weigh several tons, but the building had him beat in that regard.



We hurried to gather.  Genesis landed.



``One minute, forty-five seconds,'' Tattletale said, ``More if we're lucky.''



``Until?''  Regent asked.



``They're bombing the area,'' I explained.



Tattletale, Sundancer and Trickster found seats on Bentley's back.  Bitch climbed up behind me.  Imp materialized, for lack of a better word, dropping the effect of her power.  That left her and Ballistic.



``Three people, two fliers?'' Tattletale asked.



``Can carry one,'' Regent said.  ``Too tired to carry more.''  Shatterbird landed and wrapped her arms around him.



``I can try to carry the others,'' Genesis's voice sounded very normal considering her gargoyle-like face.  Bitch handed her a length of chain.



``One minute and fifteen seconds.  Not sure if it's paranoia or my power, but I think the bomb's going to hit closer to the deadline than not.''



Genesis gathered the chain into a loop.  As Imp and Ballistic found their seats and Genesis made motions to take off, there was the sound of shifting rubble.



``Damn it!''  Grue swore.  ``Go!  Go!'



\emph{One minute, give or take}.



We ran.  There was the sound of more rubble shifting out of place, and then a guttural laughter.  It sounded more like it came from multiple gargantuan people laughing in sync than it did from the one monster.



``More!''  His voice was even more unnatural, a jumble of individual sounds that only barely came together into something like a word.  Not so different from when I spoke through my swarm.  ``Fight me!''



The impacts of heavy footfalls were audible as Crawler broke into a run, giving chase.  They were even tactile.  He was more than a hundred feet behind us, but I could feel his impacts shake Sirius.



As my bugs struggled to catch up, my swarm sense felt Crawler stop, rearing up on his two hindmost legs.  He caught at one corner of a building and tore, twisting his body to throw a chunk of brick.



``Look out!''  I shouted.



My words were too slow.  The rock collided with Genesis, catching one wing.  She collapsed to the ground, and both Ballistic and Imp fell the fifteen or so feet to the ground.  Imp shrieked as she landed.



\emph{No}.



Crawler's pause to grab concrete had bought me time to get my bugs into position.  They swept over Crawler, laying down braided ropes of silk joined by adhesive lines and thin gossamer.  Even caterpillars began offering their assistance, using the silk they produced for cocoons.



He was a big guy, but it was a lot of silk.



I could see how it hampered his movements.  There was even something approximating surprise on his face as he dropped down so all six legs were firmly on the ground, and his forelimbs didn't extend as far as he'd expected.  He tried to run and found himself hampered further.



Crawler sported two or three tons of physical prowess, and his power had fine tuned him into a physical specimen like few others.  My bugs had millions of years of evolution to refine the quality of their silk and their ability to produce it.



For now, at the very least, I had the advantage.



``Genesis, can you run?''



``\emph{Fuck}.  No,'' Genesis spoke.  ``Made these claws for grabbing.''



True enough, her forelimbs and rear limbs were more like clawed hands than feet or hooves.



``Imp, Ballistic, run!''



It wasn't enough.  We had too much distance to cover before we could be sure of our safety.  Or of Imp and Ballistic's safety, anyways.  Even with another two minutes, or another five- well, people weren't that fast as a rule, and neither Imp nor Ballistic were runners.  It looked like Imp had hurt herself in the fall.



``Tattletale!''  I shouted.  ``Take Imp!  Bentley's strong enough to take four!''



``Got it!''  She cried, steering Bentley around and their group scooped up Imp, pulling her up onto Tattletale's lap.  Four people, but three of them were girls in good shape.



Sirius wasn't as strong, and Grue was heavy, Bitch wasn't exactly slight, and Ballistic was built like a football player.  Between the four of us, I doubted Sirius had it in him.  Not if we wanted to move fast.



``Grue!''  I called out.



``Don't you fucking dare!''  He turned his head around.



I disentangled from Bitch's grip, avoided Grue's clutching hand and slid to the ground.  I didn't land with both feet under me, so I tipped over and rolled.



``Ballistic, take my seat!''  I shouted, as I got my feet under me.  I glanced behind me at Crawler and broke into a run.



``Skitter!''  Grue barked the word.



``Just go!  I have a plan!''



Easier to lie when I was shouting, my face hidden.



They picked up Ballistic and bolted.



I was left behind in moments.



``Run, little girl!''  Crawler's broken voice carried, a rumble so low I could feel it.  ``I'll get free!  I'll catch you!  I'll hold you down and lick your skin until it melts!  I'll pluck your eyes out with the tip of my tongue!  I have your scent and you cannot ever stop me!  You cannot ever escape!''



Even the practiced motions of running couldn't take the edge off.  Running had been my reprieve for so long, my escape long before I'd had costumes and the distractions of everything that was involved there.  It wasn't doing anything to help the panic that was taking hold of me.



I wracked my mind for something, anything that might serve as an option.  Sewer?  Could I get down into the sewer or storm drain?



It was a possibility, though with the structural integrity of the city being what it was, it could just as easily be suicidal.



My bugs.  Could I lift myself up the same way I'd lifted up the small tools?  More silk, millions more bugs?



I couldn't take the chance it wouldn't work.



The one minute mark had surely passed.  I was on borrowed time, now, trusting my fate to luck.



Could Genesis form a new body in time?  It took her minutes, and I didn't have that time to spare.  She would have to find me, too.



No.  Genesis couldn't help.



And the heroes?  I searched in the direction of Jack and Bonesaw.  The heroes were fending off a group of people.  The group was larger than it had been the last time my focus was on them.  She was recruiting civilians?



The heroes were falling back, gathering in formation.  Cache was using his power, if I was judging right.  I felt some of my bugs disappear from existence as he used his power on members of his team.  Putting them in some extradimensional compartment.  The others around him, one member of the Wards, Ursa and Weld.



The good guys were preparing for an imminent bombing run.  Jack and Bonesaw were making a run for it, too.  They'd sensed something was wrong from the way the heroes were acting.



Their chances were about as good as mine.



Amy.  She was turning to run.  The others crossed her path, shouted a warning.



She used her power on the bug she was touching, making a final, haphazard connection.



My grip over the relay bugs had been tenuous.  This wasn't much better.  One bug, and I couldn't sense enough about it.  I didn't have that innate grasp of its biology, of how it operated, or the instincts that drove it.



It would have to do.



I chanced a look over my shoulder and regretted it.  Crawler was bound tighter than ever, caught by my bugs, but the look threw me off-balance.  I stumbled, nearly falling over.



I managed to keep my feet under me, righting myself, but the movement of my leg made me aware of the strain.



\emph{Come on, come on}.



We met each other halfway.  Listening to my power, it turned in midair, so its back was to me.  It skidded on the ground.



Six and a half feet long, five feet across and five feet tall.  A giant beetle.  It looked like she had used a Hercules beetle as a starting point, but built it broader, with larger, longer legs and two forelimbs with what looked like praying mantis style blades.  Sporting a black shell that looked almost ragged, the tips a gray-white, it also featured a single large horn that curved overhand, pointing down at the ground.



``Please,'' I prayed.  I swung one leg over its thorax and gripped the horn.  It was an awkward posture, making me feel like I'd fall forward and face-plant on the ground with the slightest excuse.  ``Come on.''



It ran on the ground, slower than me.  Its shell parted behind me, revealing an overlarge, complicated set of wings.  They began to beat, thrumming with sixty or seventy flaps a second, powered by an efficient machine of what I took to be a combination of biological hydraulics and musculature.



``Come on,'' I begged it.



I felt it begin to lift.  I even pushed with my toes, as if that could give it what it needed.



We accelerated, my hair whipping behind me as we gained a dramatic boost in speed.  But our trajectory was almost directly forward, not \emph{up}.  I kicked at the ground as we landed, as if that could lift us into the air.  It wasn't working.



It dawned on me why.



My bugs normally had ingrained knowledge of how to function.  This was a new lifeform.  It had all the necessary parts.  Amy had probably scaled everything up, given it every advantage in design I could want, counteracting all the problems that came with being proportionately larger.



But at the end of the day, it didn't know how to fly.



I used my power to control every movement.  I felt it accelerate again, and tilted our orientation.  I felt myself shift slightly as I found myself almost directly on top, my legs gripping the underside of his thorax, and I overcompensated.  We both crashed to the ground.  A ten or twelve foot drop for me.  My armor absorbed the worst of the impact, but I felt my forehead hit pavement.  I always thought of the concussion I'd suffered whenever I took a blow to the head.



``Come on!''  I growled the words, scrambling to my feet.  ``Don't be hurt, don't be hurt.''



He was okay.  I could examine him with my power, I just couldn't comprehend him in the same natural, instinctive manner.  It took attention, focus.  With my direction, he used a flutter of his wings and the points of his scythe-tipped claws to flip over so he was ready as I reached him.  I mounted him and tried again.  We repeated the takeoff process, faster this time.



We lifted off on the first try.  I controlled my breathing, focused my attention on him, tried to avoid that same reflexive compensation that came with a shift of my balance.



When I account for the wing compartments and the amount of space that the wings take up at the back of the shell, \emph{He's not much bigger than a motorcycle.}



Relating him to a motorcycle helped, giving me the confidence to lean gently into the turns he needed to make in shifting with the air currents.



A laugh bubbled out from between my lips, one part hysteria to two parts relief and three parts exhilaration.  I was higher up than some six-story buildings and I'd barely realized it.



Amy had heard what Grue said about our possible shortage of transportation and my lack of firepower.  She'd supplied something to serve in the time allotted, with the resources I'd provided.  She'd put this together in minutes.



Growing confident in the mechanics of flying, I swooped us down.  We were faster than the others on the ground, and we passed them with ease.  I loosened my deathgrip on the horn to extend one arm out to one side.  A wave, a salute.



That done, I pulled up.



Crawler, still bound, was unable to tear through the silk as fast as the millions of spiders were connecting it.  If there was only a way to stop the bombing, I could do something to pin him down, buy time for the heroes to arrange more permanent accommodations.



But there wasn't.  I could feel the effects as Clockblocker froze Cache in time, then froze himself.  His suit, at least.  It was only the four of them – Clockblocker, Cache, Ursa and Weld.



The bomb was about to hit, and I could only guess if we were going to be out of the blast zone.





