





In the time we had remaining, I directed my mount as high as he could manage.  My power gave me a sense of how far I was above the ground.  My range formed a loose sphere around me, and as I made my way skyward, my power covered less and less ground, on a literal level.  It wasn't long before my power didn't reach the ground beneath me.



A little daunting, being so high when I was so new to flying.



But I was \emph{flying}.  It was as close to unassisted flight as anything I could hope to experience.  I felt what he felt, his every movement was as much an extension of my will as moving my hands, blinking or controlling my breathing.



It was almost eerie, the quiet.  The buzz of signals and responses from my swarm grew as quiet as it had been since my powers manifested.  I had the capsaicin-laced bugs in my armor, a few hundred bugs stored in my utility compartment and shoulderpads, as well as the outside fabric of my costume.  I'd brought the relay bugs up into the air around me for safety, and directed everything else to find cover.  Compared to my dim awareness of the tens of thousands of bugs that I could feel from anywhere in the city, this was almost silence.



How long had I been relying on my bugs to provide sensory input?  Using my own eyes, I followed my teammates as they raced for cover.  I felt distracted, as if it was something I wanted to relegate to my bugs while I glanced over my surroundings for potential threats.



The plane wasn't as fast as I'd thought it would be.  It appeared from the clouds and crossed the skyline a distance away, at an altitude not much higher than me.  It left a muted roar in its wake, and the payload of bombs.  Black specks, smaller than I would have guessed, but more numerous.  Fifty?  A hundred?  I couldn't tell from my vantage point, and I doubted I could have made an accurate estimate.



The bombs were targeted at the parking lot where Jack and Bonesaw had been.  They detonated across the surrounding neighborhood, a carpet of explosions and flame that ripped through everything.  In a heartbeat, an area that had been drowning in stagnant water was lit up by fires that rose higher than the smallest buildings.



A wash of heated air hit me just moments after the bombs hit.  The effect on a flying creature was the same as a wave or a current in water.  It took all I had to keep from panicking, to maintain my concentration and control the giant beetle.  Rather than fight the turbulence, I rolled with it, letting it push and accepting the instability.  As it passed, I focused on righting myself and regaining my sense of orientation.



The bomb had hit close to where we'd been, but not so close that we would have been in the impact site.  That said, I wasn't sure the heat -or the shockwave, if there was one- wouldn't have done us in.



My phone rang.



``Frog R,'' Tattletale's voice greeted me.



``Leaf L,'' I replied.  ``We're all okay?''



``All of us.  Amy's here.''



``Any idea if that did anything to Jack and Bonesaw?  Or Crawler?''



``Crawler's probably taken worse.  I can picture him crawling into an incinerator and sitting in there for long enough that he can take this.''



``The fire will have undone the silk bindings,'' I said.



``Can you do it again?''



``Not here, not anytime soon.''



``Okay.''



``What are the odds that Bonesaw and Jack survived?''



``Too high.''



I stared down at the inferno.  The tallest fires had dwindled, but a carpet of fire covered everything for a five block radius.  Cars that had been mostly intact were charred hulks now, and the explosions had torn chunks out of buildings, or the flames hollowed out the interiors.  ``How would he survive this?''



``How would \emph{you} survive this?'' she asked.  ``Or- if you didn't know precisely what was happening, where would you find the most secure cover?''



I thought back to the options I had considered.  ``The sewer?  Or find a bank vault?  Not sure if the sewers or storm drains wouldn't collapse, and the bank vault could easily become an oven.''



``Places to look, anyways.''



``We can't get to them if they \emph{are} there.''



``And they can't get away, either.  Jack's slippery, but he's pinned down for the time being.  Just one second.''



I could hear other voices in the background.



A few seconds later, Tattletale was back on the phone, ``Genesis is already making a body that can withstand the fire.  Sundancer thinks she can clear away some of the blaze by flash-burning the oxygen from the area and drawing the heat and flame into her sun.  If she can, it might give us some elbow room.''



``What do you want me to do?'' I asked.



``Scout.  See if there's any clues about the opposition's movements.  If you can't figure anything out on that front, track Crawler from above.  They'll have some agreed-upon place to meet, and he could lead us to the other four\ldots you haven't seen Legend?''



``No.''



``Then I'd bet he's still chasing Siberian.  Or minimizing the damage she can do, anyways. He can't hurt her, but she's at a disadvantage as long as she has to carry that truck and protect the occupant.  Legend will know how to use that.''



``Right.''



``So Crawler will maybe lead us to the other \emph{three}.''



``On it.''  I hung up.



I'd dealt with it against Lung, I'd dealt with it against Burnscar.  Fire was something of a problem when it came to using my power.



So few bugs were alive down there.  Some had retreated beneath the pavement, or into the lowermost parts of nearby buildings, but the heat and the hot air was killing them.  Some died quickly, others slow.  I was careful about how close I got, devoting extra attention to ensuring that the beetle didn't perish or find himself unable to fly as the heat damaged his wings.



Amy had made him durable, but there was a limit to how far I wanted to push my luck when there was two hundred feet of open air between me and the ground, and a sea of fire waiting for any scenario where I managed to survive the impact.



It was a bit of a task, to focus on flying -there was no autopilot like there was with my other bugs- and to track the remaining bugs on the ground.  The sewers and storm drains were hot, but hospitable.  Navigation would be difficult for Jack and Bonesaw underground.  Between Leviathan's active destruction of the storm drains and the more passive deterioration as they got clogged with rubble and debris and flooded, there were few spaces underground where the villains would be able to navigate.



Had they died?  It was possible, and I was swiftly eliminating areas where there was both a population of bugs and space for the Nine to hide.



Crawler- I could see him prowling the streets, soaking up the flame without a care.  He was headed in the general direction of the parking lot where the heroes were, taking his time, his movements languid.



The heroes were still frozen in time, I noted.  It was hard to make them out, as they'd been at the epicenter of the blast.  Ursa was fading away, and Weld-



Weld was fighting.



Cache and Clockblocker stood frozen in time as Weld defended them against a series of attacks.  The boy's skin was glowing from the ambient heat, the fine wire strands of his hair melted into a single smooth layer.  He might have been rendered nude as the flames ate at his clothing and costume, but he wore the same fireproof suit as his teammates, the arms and upper body tied around the waist.



It was Mannequin.  Of all of them, he was the hardest to make out as he moved close to the ground, slipping between cars and through the flames to disappear from Weld's sight. He had four arms, one set longer than the other, which combined with his jerky movements to give him an almost bug-like demeanor.



I watched as he paused at the rear of one car, crouching with his two sets of arms at the bumper, then unfolded explosively, steam or vapor billowing around him as he launched the car through the air.  It wasn't much distance, only ten or so feet, but the car rolled and slammed into Weld, knocking the junior hero into his frozen teammates and pinning him there.



Weld pushed hard against the flaming hulk of the car, attempting to make room to free himself, but another car sailed through the air to land on top of Cache and Weld.



While Weld hacked at the cars, shearing through the undercarriage to make for pieces that were smaller to move, Mannequin began moving through the parking lot, pushing at more cars to get them closer to Weld and his teammates.  A minivan, a sedan, a pickup, pushed into Weld's immediate surroundings.



There was no swagger, no monologue, nothing from Mannequin but the methodical execution of his simple plan.  He approached the front of the pickup, tore off the hood and grabbed the engine block with all four arms.  Again, the billowing vapor and that explosive strength, as he brought it over his head and down on top of the second car he'd thrown, stacking them two high.  He crouched beneath the sedan and prepared to launch it as he had with the first two cars.



Cache and Clockblocker wouldn't be frozen forever.  It could be as short a time as thirty seconds.  If Cache or Clockblocker emerged from the effects of Clockblocker's power, and there were two cars piled on top of them?  It would be grim.



Worse, Cache was storing a number of the other heroes in his personal dimension.  What would happen to them if he died?



They had to have anticipated the possibility of Crawler interfering before they all recovered, but Mannequin?  I was surprised he was able to function in the midst of this blaze.



I had to remind myself he was a specialist in hostile environments, and they didn't get much more hostile than this.  He was a genius, a problem solver, and a survivor.  He was relentless, and as much as I'd managed to take the advantage in our previous confrontations, that was because he'd been out of his element, taking us on directly.



This was Mannequin's specialty: attacking from the indirect angle, at the unexpected moment to target the weak.  He favored Tinkers both because they were often vulnerable if you caught them without their gear, and for his own neuroses.



Weld managed to push the car that was pinning him from the side.  Holding the stack of vehicles up over his head, he found a point where he could set his foot without the scorched frame collapsing and kicked the car away.



As he tried to figure out how to manage the pile of flaming cars that sat atop him and his teammates, Mannequin struck.  Like a piston, Mannequin slammed into him, thrusting him away, then danced back into the cover of the flames and smoke.  Weld slid on the pavement until he collided with a car, and the cars that he'd been supporting collapsed.  At least one fell so that Cache's upper body speared through its undercarriage.  The top one tipped over and landed so it was propped up on a diagonal.



What could I do?  I didn't have a long ranged weapon.  I didn't trust my beetle's ability to hold me \emph{and} some heavy weight I could drop on Mannequin from above.



I turned around and headed for my companions.  I withdrew my cell phone.



``Need gear,'' I told Tattletale.  ``Mannequin's attacking the heroes and Crawler's approaching.''



``Got it.''



Sundancer's orb appeared in the sky, flickered, and disappeared.  A flare.  I headed in that direction.



As Tattletale had said, Sundancer was using her orb to try to clear the way.  Grue was also using his darkness, oddly enough.  The others stood by, watching, arranged so they were watching all potential avenues of attack.



I landed, and I couldn't get the beetle's legs under him to brace our landing.  He hit his stomach, his legs squashing against his underside.



``What?'' I hurried to get off him.  ``Is he okay?''



``It's a he?''  Tattletale asked.



Amy stepped forward a little, ``Its legs work through something like hydraulics.  When it's flying, it diverts those fluids to the flight system.  Do you know how hard it was to make that thing able to fly?  It's not like I've practiced this sort of thing.''



``It's fantastic,'' I said.  ``Really.  Thank you.  Do you think you could work on making him a little bigger while I get prepared?  I can supply the bugs.''



``No.''



I was midway to turning towards Tattletale when Amy refused me.  ``No?  If it's the physical limitations of something that big, then maybe the nervous system, or if you could copy over some flight instincts so I don't need to devote so much focus-''



``No, Skitter.  It's not that I can't.  I won't.''



I turned back to Amy.



She shook her head, ``This isn't a luxury.  It's not a present from me to you.  You said you needed some help escaping, you needed some mobility?  Fine.  This is it.''



``Right now, Mannequin and Crawler are attacking the Wards.  Your \emph{sister} is with them.''



I could see her expression change at hearing that.



``She's tough, she'll be okay.''



``Not in this case.  She was stored away in some other dimension by Cache's power.  If he dies before he gets her out-''



She paled.



``Idiot,'' I muttered.  ``Can't waste any more time on you.''



Before she could reply, I turned to my teammates, ``I need bombs.  Grenades, something I can drop from above and do some damage.''



``Here,'' Ballistic said.  He undid one of his belts and handed it to me.  Six grenades were placed around it.  It was too wide for my waist, so I hung it around my neck instead.



Amy stepped forward and put her hands on my bug.  I went out of my way to ignore her.



``Take this,'' Trickster said.  He drew a small handgun and handed it to me.  He pointed as he explained.  ``Ten rounds.  Thumb safety.  Grip safety.  It's my spare.''



It was heavier than it looked.  There was also a weight to it that had more to do with what the gun \emph{meant}.  I stuck it through one of the loops in my utility compartment that I hadn't used since I started out, then double checked it was firmly in place.  ``Thanks.''



I turned and climbed on top of the beetle.



``Can't make any promises, but flying should require less of your attention,'' Amy said.



``Okay,'' I said.



``So you focus on helping my sister.''



``I'll help anyone that needs it,'' I said.  With one false start, I managed to take off.  I stayed low to the ground for as long as I could, to try to judge what Amy had done to the beetle.



There was some underlying logic, but it wasn't the same sort of instinctual behavior I was used to.  As far as I could tell, she had set him up to continue whatever I'd last instructed him to do, so I didn't need to maintain focus to keep him going.



I frowned and suppressed that instinct.  As it stood, it was dangerous.  If he was flying and I got knocked out, he might keep flying.  The same might apply if I was turning, or adjusting to compensate for my weight and got distracted partway through.



No, after testing it I didn't like how slippery it made the navigation feel.  I'd only use it on a case-by-case basis.  Besides, it was something I could do with my power anyways, with greater effect and nuance.  I'd been knocked out once, and my power had continued directing insects by my last given order.



Irritating.



I hurried back to the scene of the fight.  Clockblocker's power lasted anywhere from thirty seconds to ten minutes.  Weld had been on the defensive when I'd left, and the Wards were relying on pure chance to determine if they'd make it out of this okay.



I could hear the fight before I could make anything out through the smoke.  The fires were still burning, but most seemed to have burned through whatever fuel sources they'd found. Beyond what was in the bombs themselves, anyways.



It was probably dangerous to be taking in too much smoke, both for me and for the beetle, but I had to be close.



There were crunching sounds and the noise of metal striking metal.  I directed the beetle around one particularly thick cloud of black smoke and saw Weld hacking the cars to pieces, his arms a pair of oversized blades.  Mannequin threw a car at him, and Weld lunged forward to slam it down into the ground with both hands.  Mannequin used the opening to leap forward, his feet momentarily resting on Weld's shoulders, before he hopped down to the ground.  Spools of chain unfolded in Mannequin's wake, and he bound Weld, dragging him away from his allies.



Weld had undone much of Mannequin's setup, but there was still one flaming truck leaning against Cache.  It was heavy enough to crush Legend's teammate beneath it if Clockblocker wasn't quick enough to reach out and freeze it.



Carefully, I positioned myself, noted the wind, and then grabbed a grenade from the sash that hung around my neck.



\emph{I really shouldn't be using this without any training}, I thought.



I pulled the pin free, then dropped it straight down.



Wind carried the grenade further than I expected.  It landed somewhere a few feet behind Cache, rolled, then detonated.  The car that had been propped up against Cache was thrown off, rolling onto its roof.  The other debris scattered.



I felt a wave of relief that I hadn't managed to hit them with the grenade \emph{just} as they came out of stasis.



Mannequin backed away from Weld to stare up at me.  Weld, for his part, had absorbed the metal of the chains and disconnected the excess from his body.  When he reshaped his hands into weapons, it was faster than I'd seen him do it during our attack on the PRT headquarters.



Weld gave me a salute, using a knife-hand that was as long as he was tall.



We went on the offense, going after Mannequin.  I used two more grenades to drive him out of cover and to stop him from flinging any more cars at the heroes, while Weld maintained the pressure by constantly closing in.



Both Weld and Mannequin had seemingly unlimited physical reserves.  Both had equipment they could spring from nowhere – Mannequin had his concealed equipment and weapons, Weld had his crude shapeshifting abilities.



That wasn't to say they were evenly matched.



Mannequin could have hit Weld with everything he had, and I doubted he would have even slowed Weld down.  The opposite wasn't so true – I suspected that one solid blow from Weld would leave Mannequin a wreck.



The problem was that even though Weld was strong, he was heavy, and this put him somewhere near the upper limits of what you'd expect an athlete to be able to perform.  Mannequin, by contrast, was faster than any olympic runner, more agile than any gymnast.  He could contort and slide through the space beneath a car, change directions on a dime, and that was without getting into the other advantages he brought to the table.  I suspected he could see through the fire and smoke, and where Weld's shapeshifting was largely limited to hitting stuff, Mannequin could use his arms like grappling hooks to cover more ground and keep his distance.



If we had any advantage, it was that we were buying time.  Mannequin couldn't stop to throw vehicles at the frozen heroes.



The counterpoint to that was that Crawler had heard the commotion and was approaching.  He shifted from a walk to a head-on charge as he got a block away.



``Crawler!''  I shouted the words at full volume.  Weld snapped his head up to look at me, and I extended one arm out to inform him on the direction.



The problem was that Mannequin could hear too.  He shifted positions and prepared to heave another car at the heroes.



I pulled the pin on another grenade and lobbed it in Mannequin's direction.



Call it chemistry, rhythm, or just the nuances one picked up after fighting alongside someone else, there was a flow to working with a member of your team, a way I could trust others to have my back and vice versa.  Weld and I didn't have that.  It was \emph{my} understanding, my assumption, that the bruiser would take on the heaviest hitter on the opposing side, and the others in the team would focus their efforts on the secondary threats with using utility and technique.  It was how the Undersiders tended to handle matters.



Weld\ldots I don't know what his assumption was, but maybe he was used to having people like Clockblocker and Vista handle the most threatening and problematic enemies, while he threw himself at the enemy ranks and drew the secondary fire.  Maybe they were even tactics he'd been drilled on with his previous team.  Maybe he was too focused on protecting his teammates from Mannequin and didn't trust me to handle it.



I didn't know what his reasons were, but Weld turned toward Mannequin in the same moment the grenade left my hand.



It was disastrous on two levels.  Whatever surprise I'd hoped to retain was lost when I was forced to shout out, ``Grenade!''



Mannequin abandoned his hold on the car as he leaped to one side to get clear well before it exploded.  Weld, too, managed to stay out of the way, stopping in his tracks.



Crawler came tearing through the blazing parking booth and blindsided Weld.  In terms of raw power, the junior hero might as well have been a powerless human for all the defense he could muster.  Crawler's claws tore into him, revealing bones in silver, organs in copper and gold.



Two grenades left.  I threw one down at them.  Mannequin backed away, and Crawler, though his head was directed at Weld, rose up onto his two hind legs and batted at the grenade with Weld's body.



The explosive went off a second after the impact, and Weld was thrown free of Crawler's grip.  I saw him stagger to his feet, his wounds closing as he shapeshifted them.  He couldn't do much about the material that had been raked off of him.



This wasn't going well.



Mannequin made a gesture at Crawler, fingertips of two hands all touching, pressed to his `mouth', then he pulled his hands away, splaying his fingers.  Crawler cocked his head and Mannequin pointed at the frozen heroes.  I heard Crawler rumble with guttural laughter.



\emph{No}.



What could I do?  I was a bystander here, effectively powerless, but for my beetle.  I had the gun, but it wouldn't do anything to Crawler and I didn't trust myself to hit Mannequin at this range.  I had a single grenade, and I knew that wouldn't even make Crawler flinch.



Crawler spat a caustic spray onto Cache and Clockblocker.  I could see the mucus fizz and pop from my vantage point high above.



If I used a grenade, could I clear it away?  Or was it too viscous?  Would I be losing something I couldn't afford to throw away?



I didn't get a chance to see.  Cache came to life.



I couldn't even imagine what went through his mind.  He went from disengaging from a fight with Jack and Bonesaw in a flooded parking lot to facing down Crawler and Mannequin in the middle of a sea of fire.



Maybe he'd anticipated that, but he couldn't have anticipated the acid spittle.  Holes began to appear in the fabric of his fireproof costume.



He managed to maintain his composure- I had no idea how.  I couldn't imagine how it must have felt to be down there, feeling the heat and smoke coming in through the widening holes in the fabric.  He began using his power, calling up the shadowy geometry that would deposit the heroes onto the battlefield.



The two members of the Nine, it seemed, didn't intend to give him the chance.  Both charged for the hero.



This time, at least, Weld took on the heavy hitter.  He leaped at Crawler from the side, his hand becoming needle-fine as he plunged it into one of Crawler's largest eye sockets.  I knew that Crawler could dodge Ballistic's hits.  He must have seen Weld coming and simply not cared.  The needle barely penetrated Crawler's eye, but Weld used the leverage to wrap himself around Crawler's face.



I drew the gun and leveled it at Mannequin's back.  He was running in a straight line, I remembered to click the thumb safety, squeezing the handle with both hands to get the grip safety on the back of the gun, and put him in the crosshairs, leading just a bit.  I could remember the tip you always heard in the movies.  Squeeze, don't pull.  Exhale as you squeeze\ldots



Visions of the dead Mannequin had left in my district flashed through my mind's eye.  The paramedics, the bitchy old doctor, the people he'd gassed.  \emph{My} people.



I could feel the recoil jolt its way through my arms to rattle my body at its core.



Mannequin fell.



\emph{How the hell did I manage that?  }Between the recoil and the shock of what I'd just managed, it was all I could do to stay seated.



I aimed and fired again at his prone form, the shot going off just before he rolled to his feet.  I couldn't make out if I hit or not.



Crawler was distracted just long enough for Cache to bring out the first heroes.  Glory Girl, Prism, Miss Militia, Triumph\ldots



Weld tumbled to the ground, and switched targets to the retreating Mannequin.  Maybe he'd coordinated something with the others.  I couldn't say.  Glory Girl, in her all-concealing fireproof suit, certainly seemed ready to serve as the frontline defense.



I was so busy tracking Mannequin, looking for an opportunity to shoot him again, that I nearly missed what happened next.



Crawler got close enough for Glory Girl to swing a punch.  She took the bait and swung, then twisted in mid-air to deliver a kick.  He pulled just out of reach of both hits, then opened his mouth to retch spittle and bile all over her.



It had the same effect on her costume that it did on Cache, only far, far faster.  In moments, she was down to the skin-tight costume she wore beneath her white and gold dress, her forcefield protecting her.



I pulled a grenade free.  Maybe it could distract him long enough for her to-



Crawler surged forward, slamming his head into her.  Like a spiked volleyball, she slammed hard into the ground.



I could see her skin turning red, then black, where the spittle had covered it.  Flesh melted away to reveal muscle, then the acidic vomit began to eat away at \emph{that}.  She screamed, frantic, thrashing, oblivious to the flaming patches of ground that she was rolling into.



The bugs I'd placed on my teammates told me they weren't close.  Glory Girl and Cache were down and needed immediate medical attention – Cache had managed to call in the rest of the Protectorate and the remaining Wards, but he'd collapsed into the arms of one of the adults.



Crawler paced forward with an almost anticipatory slowness.  I could make out his tongue, licking around his lips.



This was going south fast, and I wasn't sure what I could even do.





