





``Wards!''  Weld hollered.  ``Crawler and Mannequin, like we discussed!  Close ranks around Victoria!''



His words broke the spell that the scene had over Vista and Flechette.  Surprising that there were so few Wards here, on a level.  Kid Win wasn't in sight, nor was Chariot, and Clockblocker was under the sway of his own powers. Shadow Stalker, Aegis, Gallant and Browbeat were dead or gone.



The final sorta-maybe member of their group, Glory Girl, was being eaten alive by Crawler's acid.



Vista and Flechette moved to positions just behind and to either side of Weld.  The group blocked Crawler's view of Glory Girl.



Miss Militia directed the adult heroes with a series of short commands and hand signals.  Ursa and Assault led the way with Miss Militia, Prism, Battery and Triumph following, clearly aiming to flank Crawler and close the distance between them and Mannequin.



Crawler spat, and Vista used her power, reducing the distance the spit traveled to a tenth of what it might have been.  Crawler leaped, and she widened the distance between him and everyone else so he stood in the midst of a clearing.



Flechette fired a bolt straight into Crawler.  It penetrated his face and stuck there.  Little surprise on that front; I'd seen her stick \emph{Leviathan} with one of those giant needles.  Crawler's face bubbled around the wound where it was rejecting the foreign object.  Almost imperceptibly, it began to slide out.



He rumbled with a low, guttural laugh, mocking.  Was he enjoying himself?  He was a masochist, and it was the rare thing that could hurt him.



Miss Militia interrupted his gloating with a shot from a rocket launcher.  His claws dug deep into pavement as he resisted being knocked over.  She used her power to reload the rocket launcher and shot him again, uprooting him.  Triumph used a full-power shout to send Crawler sliding across the clearing Vista had made.  Vista widened the distance by stretching the landscape.



Prism and Battery went after Mannequin.  Prism split into three copies of herself, complete with fireproof suit, closing in as Battery used her power to cross the distance and trade blows.  I was only peripherally aware of Prism, given how she was based in New York, but seeing her in action reminded me of how she operated.



She was a self-duplicator, always producing two other versions of herself, but there were nuances.  So long as one duplicate lived, she would survive whatever happened to the others, but they didn't last long.  She could also expend them to enhance herself.



It made her an effective partner for Battery.  Both were all about the setup followed by execution.  Prism formed her duplicates and spread them out while Battery attacked, then drew her duplicates back into herself in a flash of light before delivering a crushing strike.



Mannequin was holding his own.  The hits that did land seemed to have little effect, as he went limp and bent with them.  It seemed he was keeping to the old adage of a supple willow bending in a hurricane that topples a sturdy oak.  Even when Battery was moving at super speed, he was quick to take the advantage of a kick that went too high or a sweep aiming to knock his feet out from under him.  He ducked beneath the former and hopped over the latter, then using his grappling-hook hands to haul himself a distance away.



He managed to get close enough to cut down two of Prism's duplicates, then pointed his hand at her third self, extending a blade from the base of his hand and firing it like a harpoon.  Battery used up her charge and swept it aside before it could strike home and finish off the heroine.



Ursa, Triumph and Assault were getting into the thick of things with Crawler while Miss Militia and Flechette aided them from a distance.  Ursa was creating forcefields in the rough shape of bears, two at a time.  Weld stood, defending the two female members of the Wards.  Glory Girl was looking worse for wear with every passing second.



``Weld!''  I shouted, drawing the beetle as close as I dared with the heat and smoke beneath me.  ``What can I do!?''



``More bombs on Mannequin!''  He shouted.



``I'm out!''  I replied.



``Then get out of here!  You'll be one less person we have to protect!  Our front line's pretty thin!''



Weld half-turned to glance back at Glory Girl, and I could see his expression change as he saw how bad she was.  It was reaching the point that we might have to leave her for dead. There were spots where the muscle had necrotized enough that I could make out her internal organs.  If the redness was any indication, the acid was extending to her vitals.



``Evac Victoria and Cache on your way out!''



Evac.  The last time I'd had a scale to check, months ago, I'd weighed a hundred and eighteen pounds.  With my gear, my costume, maybe that added up to one hundred and twenty.  I had my doubts the beetle could manage me if I was even ten pounds heavier.  How could I carry someone larger than me, in addition to myself?



Maybe I didn't have to.



Had to think out of the box.  If I could get her out of here, and if the beetle could manage her, I could remotely pilot it to Amy.  Those were two pretty huge ifs.  No, couldn't pin my hopes on that.



I saw Cache using his power on himself.  He was barely able to crawl, but he surrounded himself in his dark geometry, disappearing as it condensed down to a point.  He'd taken himself out of this dimension.  I wasn't sure if it was a journey of no return or a way to get some respite.



But his use of his power gave me another idea.  Glory Girl had powers too.



``Can she fly!?''  I shouted.



``What?''  Weld asked.  He glanced up at me, then turned his attention back to the fight.  His body was tensed and ready to act the second Crawler made a move for his teammates.



``Ask her if she can fly!''



``She's insensate!''



``Try!''



He turned back to the superheroine and said something I couldn't make out.



If she responded, I didn't hear it.



Weld extended his arms into two long poles.  They extended ten feet, then fifteen, then thirty.  Reaching back, he caught Glory Girl with the ends, bending the tips to encircle her body.



``Wait!'' I said.



He glanced up at me, then over at Crawler.  The villain was spitting at Assault, who slid on the ground to evade the spray.  Crawler took advantage of the gap in the defensive wall to stampede toward Vista and Flechette.  Vista increased the distance, but not as fast as Crawler crossed it.



Under pressure, choosing the protection of his teammates as his top priority, Weld ignored my plea for a moment to think.  He twisted his entire body to haul Glory Girl into the air, throwing her at me like a catapult might throw a boulder.



I changed my orientation so I'd be ready to catch her.  Rather than try to wrap my arms around her, I moved so we were racing alongside her as she arced through the air.  It gave me only a second or two to make the call about grabbing her.  I didn't want to get that acid on me.



I grabbed at the two things that seemed safe – the intact portion of her lower costume and her hair.  I pulled back, hauling on both, but the beetle wasn't able to offer the necessary lift.



She was insensate with pain, and she struggled at what I was doing to her.  I momentarily wondered if she'd hit me or the beetle with one of those punches that could crush stone. Worse, if she grabbed me and I couldn't break away, I'd plummet to the ground with her.



``Fly!'' I screamed the word.  ``Lift up, Glory Girl!''



Her face was melting on one side, her eyes a ruin, her ear and the surrounding area of her head a bloody mess.  I wondered if she could even hear me.



I was getting dragged down.  How long before I had to make the call about letting go?  It would mean letting her fall back into the burning city street.  Maybe her forcefield would protect her, but the acid would continue to eat into her, until it got at something especially vital.  She would die, slowly and painfully.  Burning to death would almost be a mercy.



``Rise!  Fly!''  I shouted.



She began to lift up.  I took the opportunity to let go of her hair, grabbing at the one hand that wasn't covered in acid.  I pulled on her hand, and she followed my lead.



We moved as fast as my beetle was able.  I knew she could fly faster, would have compelled her to even push me and the beetle forward if I thought I could have handled the navigation.  As a group, we passed over a red scaled wingless dragon that I took to be Genesis, wading through the flames on her way to the site of the battle.



My beetle needed a name.  Had to have a better way of referring to it.  A hercules beetle, but bigger, a giant.  I thought about Hercules, about the myth; Hercules had borrowed the burden of the giant who carried the world.  Atlas.



``Come on, Atlas,'' I urged him, ``Faster.''



Dumb to talk to him, when I knew for an absolute fact that he couldn't understand me.  Maybe I was talking to myself.



We found my teammates still clearing a path through the edge of the area.  They were all walking, the dogs in a formation around them, Bitch holding up the distant rear with Bastard.



I landed.  Glory Girl didn't have the strength to stand, and collapsed like a rag doll.



``Holy shit!''  Regent said, as he saw the extent of the damage.



Amy went white as a sheet.



``Heal her!  Just don't touch the spots where the acid hit her!''



``I don't know- what happened?''



``Crawler spit on her, then knocked out her forcefield.  \emph{Move!  Fix your sister!}''



She staggered forward and reached out toward Victoria.



``No,'' Victoria mumbled.



``You're dying,'' Grue spoke.



``No,'' Victoria repeated herself.  ``Not--''



She coughed sharply and mumbled in the same breath, and didn't bother trying to correct herself.



``Do it anyways,'' Tattletale said.



Victoria swung with her good hand, slamming it into the sidewalk.  Cracks spiderwebbed out from the impact site.  She coughed.  ``No.''



``If she hits me, she'll kill me,'' Amy said.



``Okay,'' Tattletale said.  ``If she doesn't want help, you shouldn't give it.''



``She's not thinking straight.  What I did--''



``Doesn't matter,'' Tattletale said.



Amy shook her head, talking over her, ``She's always been emotional, passionate, unrestrained, and she's channeling all this new emotion into \emph{hate}, because it's the closest equivalent.''



``New emotion?'' Regent asked.  ``You mean you mindraped her.''



Amy looked like she'd been slapped across the face.  I wasn't \emph{surprised}, but hearing it said out loud was unsettling.



``Seriously?''  Imp voiced the incredulity that everyone else seemed to be feeling.



``It was an accident,'' Amy said.



``How do you do that by accident?''  Imp asked.



``Enough,'' Tattletale cut in.  ``Victoria, listen, I'm going to pour some sterile water over you, and hopefully it'll flush some of the acid away, okay?  I don't know what else we can do for you.  I know you can't see, so don't be surprised when it happens.''



Victoria turned her head slightly, but she didn't respond.



``Okay,'' Tattletale said.  She didn't have water in her hand.  Instead, she grabbed Amy and shoved her in Glory Girl's direction.  Amy looked at her, scandalized and horrified, but Tattletale only mouthed the word `go'.



Amy knelt by her sister and touched her hand.  Glory Girl's back arched as if she'd been electrocuted, and then she went limp.  Paralyzed, unable to resist.



``I'm sorry,'' Amy said.  ``So, so sorry.  Oh god, this is bad.''



None of the rest of us spoke.



``I can't- can't figure out what this venom is.  I can't touch it to see if it's organic, um, I can only see what it's doing.  At least part of it is enzymes.  It's denaturing proteins in her cells and using the byproducts to build more enzymes, and it's breaking down lipids as a side effect, shit.  Oh god, and there's more to it.  The fluid the enzymes are swimming in is some kind of acid.''



``Can you fix her?''  Tattletale asked.



``So much to do,'' Amy mumbled, ``Have to counter the acid with some kind of physiological byproduct, have to stop the enzymes from liquefying her entire body, and repair the damage.  Trying to make some kind of firebreak to stop the spread of the venom, withdraw the proteins the venom is using to propagate itself.  There isn't enough tissue in her body for everything I need to do to fix her.''



``Fixing her body and healing all the damage can come later,'' Tattletale said, as if she were reassuring Amy.  ``For now, keep her alive and fix what you did to her head.''



``I have enough to manage without worrying about that.''  There was a note of desperation in Amy's voice.



``It's as much a priority as anything else.  I said it before, if you don't do it now--''



``Shut up,'' Amy snapped.  ``I need to focus.''



We watched her work.  The dissolving began to slow, then fix.  The wounds weren't closing, but the necrotized edges of the ruined flesh was turning from black to crimson.



``You going to go back?''  Tattletale asked me.



I shook my head and glanced over to where the clouds was glowing orange with the reflected flames.  ``Nothing I could do.  Too much fire, it cancels out my power, and it's dangerous for Atlas.''



``Atlas.  I like that.''



I shrugged.



I turned to Amy.  ``Do you want me to bring bugs?  Maggots eat only dead flesh, which might be helpful if--''



``No.  I can handle that.''



``Or I could get some of the more useless bugs, like the ones you used to make Atlas, for raw material.''



Amy turned to give me an incredulous look.



``You said you didn't have enough tissue to patch everything together.  If you wanted to put together a placeholder\ldots''  I trailed off.



``Nice,'' Regent said.  ``She could be a human-spider hybrid.  Add some insult to injury with the mindrape thing.''



I could see Amy tense.



``That's not what I'm saying,'' I told him.  ``Amy was saying the enzymes were dissolving proteins and other stuff.  The bugs would be a source of protein, vitamins, carbs\ldots''



``I'm a little surprised you know that,'' Grue commented.  He didn't take his eyes off of Amy and Glory Girl.



``My power tells me some of it,'' I said, ``And I did some reading after we took over our territories, trying to research that stuff.  It was an idle thought, but I was thinking that if we got into a food shortage, I could feed my people with bugs.''



Imp made a gagging noise.



``Wow,'' Regent said.  ``See, you just started off by making me think you were warped and creepy because you were suggesting Panacea turn Glory Girl into some sort of bug-borg, and now you're making me think you're creepy and weird because you wanted to feed bugs to people who \emph{aren't} your enemy.''



``It was just an idea,'' I said, maybe more defensively than I should have, ``And bugs are nutritious.  People all over the world eat them.''



``Have \emph{you}?'' Grue asked.



I shook my head, ``But I would have tried them first, if I decided to go ahead with that plan.''



``Please,'' Amy cut in.  ``Can you?''



I turned to her.  It took me a second to realize what she meant, after the line of questioning from the others.



``Yeah, of course,'' I told her.  I began calling a swarm to me.  I'd already exhausted the surrounding area of most, and the ones I hadn't already called forth were buried in the deepest recesses and most awkward areas, where it was so inefficient and time-consuming to bring them to me that I'd left them where they were.



It took some time to bring them to the area.



``How was the battle going?''  Grue asked.



``The heroes seemed to be managing, but I don't know how things are going to turn out,'' I said.  I looked at Shatterbird, who floated above us.  ``We could use her help.''



``Don't trust myself to control her if she's too far away,'' Regent spoke.



I made a face.  ``Right.  But she could carry you?''



``She almost dropped me once before.  It's pretty hard to hold on to someone, especially without the leverage you have when you're on the ground.



The first bugs were arriving in front of Amy.  She began dissolving them into their constituent parts and pressing them into Glory Girl's abdomen.  When she raised her hand, they were gone.  She held her hand out for more to gather while keeping one hand on Glory Girl.



Minutes passed before Amy stood and wiped her bloody hands on her pants.  ``Done as much as I can.''



Glory Girl didn't look `done'.  Scars crawled across her body, angry-looking, surrounded by burns from the acid and flames.  Her skin in areas where the flesh had melted away was so new and stretched so thin that it was translucent, and there was little to no body fat to pad the area between skin and muscle.



``Fix her,'' Tattletale said.  ``You know what you did to her, you know it was wrong, undo it and walk away.''



``Can't,'' Amy shook her head, ``I said I've done as much as I can, but there's so much more I need to fix.  The parts I made with the bits I took from bugs will need to be replaced with real flesh.''



``That's her choice.  You saved her life, good on you, but you need to let her make the call.''



``Why do you care so much?  You're a bad guy.''



``Oh yeah,'' Tattletale replied in a dry tone, ``I'm \emph{evil, }right?  Maybe that's all the more reason to listen if I'm saying that something's fucked up and wrong?''



Amy shook her head, ``She needs to eat, and I need to rest.  I can speed up her digestion, like I did with breaking down the bugs inside her.  But I need so much material that it's going to take a lot of food if I'm going to get everything she needs.  One night, and I can make her normal.''



Tattletale shrugged, ``That's fine.  Just undo what you did first.''



``If she fights me and doesn't let me finish--''



``That's her choice.''  Tattletale repeated herself.



``No!  That's- that's not her.  That's the change I made doing the talking, or the aftermath of it.  Even if I removed all the neural connections that have been made since, there's so much more in the emotional cocktails and hormonal balances.  She's channeling it into anger instead of\ldots instead of love.''



\emph{Love}.  The implications were so fucked up.  It was the sort of thing \emph{Heartbreaker }did.



She hugged her arms against her body.  There were tears in her eyes.



``You need to fix her mind \emph{now}.  For you, not for her.  Maybe she'll forgive you at a later date, when she's thinking clearly again,'' Tattletale said.  ``Maybe then she can approach you, you two can start interacting again, you rebuild that trust over months or years, and you can finish healing her body when she gives you her permission.''



``Or I can fix her \emph{now}, undo what I did and then walk away forever, because I don't deserve forgiveness and she shouldn't have to live like this because- because a wrong \emph{I} committed fucked with her focus or made her too aggressive or--''



``It wasn't like that,'' I said.  ``She didn't have time to react.  I was watching.  These injuries Crawler inflicted were not your fault.''



``Doesn't matter.  She would have reacted sooner if she'd been getting enough sleep, if her emotions weren't off kilter.''



``Amy--'' I started.



She shook her head so violently that I stopped mid-sentence.  ``I can almost feel right about this.  I patch things up, and then I go.''



Amy bent down and touched her sister.  Glory Girl stirred and sat up.  With Amy's help she stood.



``You're lying to yourself,'' Tattletale said.  ``And you're making things worse.''



``Just- I'm just keeping her complacent.  I'm okay with it if she doesn't forgive me for it.  Don't deserve it anyways.  I do this, and then I'll go somewhere I can be useful.  Only reason I haven't made more of myself and my power is because of the rules and regulations about exploiting minors with powers.  Either go into government or don't work at all, and didn't want to go into government because they would have made me a weapon.  And because I needed to be with my family.''



She smiled, but it wasn't a happy expression.  ``Burned that bridge.  But I'm sixteen now, I can get a job somewhere, start making a real difference with my power.''



``And the last thing you'll do for your family is this?  Hypnotizing your sister when she's already mad at you for assaulting her and fucking with her head?''  Tattletale asked.



``The last thing I'm going to do is fix her.''



``A means to an end.''  I stepped forward a little. ``Trust me when I say I've been down that road.  I don't recommend it.''



``You don't understand.''



``Wasn't it only a little while ago that you admitted you couldn't figure out what you needed to do to put things right?  You asked me to make the call.''



``Because you had the experience in making calls on morality in dangerous situations, situations where I can't even think straight,'' Amy said.  Her voice hardened a little, ``But I have the impression that you don't have that same expertise when it comes to \emph{family}.''



I thought of my dad, and it sat heavily enough in my mind's eye that I couldn't formulate a response.



Grue formulated one for me.  ``You're one to talk.''



``I'm trying to fix this!''  Amy raised her voice.  ``Why are you making this a thing?  Why do you even care?''



Tattletale shrugged.  ``I talked about it with Grue, Bitch and Regent.  We were considering offering you a place on the team.''



I looked at Tattletale in surprise.  I glanced at Bitch.  \emph{Even her?}



Amy scowled, ``As if.  You're such hypocrites.\emph{  Regent} mind controls people all the time!''



``Regent mind controls the monsters, the bad guys,'' I said.



``Taking advantage of bad people for selfish ends.''



``What \emph{you're} doing is selfish,'' Tattletale cut in.  ``You think you're doing it for her, but you're only doing it to soothe your own guilt.''



``No,'' Amy said, as if that was that.



She glanced at me.  ``Thank you for bringing her to me so I could help her.  Um.  I don't want it to be a nasty surprise, so you should know I didn't give the bugs I designed any proper digestive systems.  They'll starve to death before the week's over, but the Nine will be gone by then.  If they aren't, we're all fucked anyways, aren't we?''



I looked down at Atlas, then back to her.  I clenched my fists.  ``I'm using them to \emph{help} people.''



``For now, sure.  In the future?  I couldn't be sure.  So I put a time limit on them.  Let's go, Victoria.''



``Hey!''  I shouted.  My swarm stirred around me as the pair turned to walk away.



``No,'' Tattletale said, putting a hand on my shoulder.



``But she--''



``She's not thinking straight.  We've all been there.  You don't want to start a fight.  We've got other enemies to focus on without making more.''



I was pissed off enough that I wanted to hit someone.  I couldn't even articulate the entirety of \emph{why} I was so angry.  I'd gone out of my way to be nice to her, to empathize, to save her sister, and save both of their lives.  And \emph{this} was how she repaid me?  A slap in the face, a final gesture to make her distrust for me as blatant as possible?



``I could try,'' Grue said, ``I've seen her power, but I don't get the full picture, I might kill it.  Or fuck it up somehow.''



``Please,'' I said.



He raised one hand and created a wave of darkness.  It passed over the two girls.



I brought Atlas to Grue, and he laid one hand on the shell.  I could feel shifting in Atlas' mandibles, head, thorax and abdomen.



The shifting stopped the same instant I saw Glory Girl spear straight out of the top of the cloud of darkness, flying high with Amy in her arms.



``Did you finish?''  I asked.



``Couldn't say,'' he sighed.



I searched Atlas with my power, trying to get a feel for his physiology.  As with all the other instances, everything about him was invisible if I wasn't looking specifically for it, a black hole in the database of knowledge my power provided.  He was created, and there was no genetic blueprint that my power could decrypt and analyze to figure out what part served a given function.



When I reached the area Grue had affected, I found it even darker, untouchable.  The nervous system wasn't something my power could interface with.



``I had to model it off of something, and I get the feeling I don't have the same innate knowledge that Panacea does,'' Grue told me.  ``The only thing I have any knowledge about is myself.  I don't know if it's going to work, but he has a human digestive system.  Or something close to it, that worked with his body.  Near as I can figure, everything connects to what it's supposed to.''



``Thank you,'' I said.  ``Really.''



Tattletale was still watching Glory Girl and Amy disappear.  She glanced down at Atlas, ``You'll have to figure out a diet that gives him every nutrient he needs, and pay a hell of a lot of attention to him.  If you give him something his body can't process, it could poison him like that.''  She snapped her fingers.



I nodded.  It was still better than nothing.



Sundancer was still clearing a path.  I climbed on top of Atlas and rose above the ground, swaying a little in midair as I tried to control his flight enough to hover.



``Go,'' Grue said.



``What?''



``Scout, search.  Check on the fight.  You're restless.''



``Don't like how that thing with Panacea ended.''



Grue shook his head, ``Me either, but we should focus on what we can do in the here and now.''



``And I'm restless because I'm frustrated.  There's nothing for me to do here.  I can't handle the fire, can't do anything if I'm with you guys.''



``Search for Jack and Bonesaw so we can put them down,'' Regent said.



I shook my head.  ``They disappeared.  Literally.  I'm not sure if they're dead or if they found a hiding spot.''



``That's something we can work on,'' Tattletale said.  ``Siberian was heading to a destination, right?  Heading southeast?''



``Sure.''



``Did you see what direction Jack and Bonesaw were headed?''



I nodded.  ``Northeast from a point a few blocks that way.''  I pointed.



``Then I think I know where they went.  It's quite obvious when you think about it.  A place they could have researched in advance, unoccupied by anyone of consequence, capable of withstanding hits from virtually anything, supplied with food and water\ldots''



Obvious?  Maybe only to Tattletale.  Still, with her hints, I could follow her line of thought to its conclusion.



``The emergency shelters for Endbringer attacks,''  I finished for her.





