





``Three places nearby they could have gone,'' Tattletale said.  ``Two that fit with the direction they were running.  The shelter underneath the central library, and the one near where Scion confronted Leviathan.''



``I remember that one,'' I replied.  We were walking at a brisk pace around the perimeter of the bomb site.  The area to our left still burned, and Sundancer was in the lead, clearing away the worst of the fires ahead of us.  I was walking with Tattletale and Grue, Atlas following behind us.  The others rode the dogs behind me.



``If we're going to check those locations, then\ldots'' Tattletale trailed off.



``If I had a preference, I'd rather we check the library first.  Bad associations with the other spot.''



Tattletale turned her head at that.  ``I thought you'd be proud.''



I shook my head.



``I only heard secondhand, so I didn't get the full story, but you stabbed Leviathan with Armsmaster's weapon and distracted him from going after the civilians that were inside that shelter.''



``Don't know how many I really saved.  He had a good thirty seconds to a minute to unload everything he had on the people in there, and we all saw how much damage he did to some of our toughest \emph{capes}.''



Tattletale nodded.



``I dunno.  I think of what happened back then, and I get this ugly feeling in my gut, like I did something wrong, or I didn't try as hard as I could have because there was someone in that shelter who I sort of hate.  Hated?  I'm not sure if I should use past tense.''



``One of your bullies?''  She asked.



``Teacher.  I think that when I left the Undersiders, I guess I was thinking of considering becoming a hero or something.  But with what happened at that shelter, I almost feel like it was the turning point.  It was the first time I did anything that someone else could point to and call it heroic, and somehow I can't find it in myself to be proud about it.  And it's like, that dream of being a hero that I always had just kind of faded away in the face of reality.''



``We're glad to have you, whatever your reasons,'' Tattletale said.



``Thanks,'' I told her.



I looked at Grue.  ``You okay?''



``I'm getting annoyed that people keep asking that,'' he spoke.



``Don't be a dick,'' Tattletale replied.  ``She's asking because she cares.  \emph{We're} asking because we care.  And you \emph{know} that if it was one of us that went through what you did, \emph{you'd} want to make sure we were in the right headspace to go up against the Nine.''



Grue sighed, but he didn't respond.



``You'd tell us if you weren't feeling right, yeah?''  Tattletale asked.



``If I had any idea what I felt, and it wasn't good, yeah.''



``Good enough.''



We watched as Sundancer cleared away the flames with her flickering sun.  Flames bent toward it as if being influenced by a strong wind, thinned out and disappeared.



She cancelled out her power and turned back to us.  ``One minute to cool off and we're probably okay to go!''



``We should decide where we're going and how we're going to make our approach,'' Grue spoke.



``If they're waiting for their teammates, they'll stay inside the shelter for the time being,'' I said. ``We'll be in a better position if we don't try anything overly complicated, like a pincer attack, if there's more than one exit.  We can hit them hard enough with Sundancer, Ballistic and my bugs.''



Grue nodded.  ``I don't disagree.  You two will have an idea if they're making their way out the other exit.''



``The two shelters are close to one another,'' Tattletale said.  ``But I'm still a little worried they'll leave one location while we're checking out the other.  I almost want to split up.''



``Is that worth the risk of having half our group caught off guard by the Nine before the other half can arrive?''  I asked.



``A better question,'' Tattletale said, ``Is whether we can afford to let them get away.  If we miss this chance to go on the offensive and let them escape, they go into hiding and work out a strategy.''



``And we're not exactly in their good books,'' I said.  ``So we'd be a primary target.''



Was I imagining it, or did Grue's darkness expand around him by a fraction?



``Sorry,'' I told him.



``Hm?''  He turned towards me.



No use making it worse, if I was prodding a sensitive area by raising the threat the Nine posed.  ``Nevermind.''



``Saddle up!''  Tattletale called out.



Sundancer turned and sprinted back to the dogs.  Regent hopped down from his seat and grabbed Shatterbird's wrists so she could lift him into the air.  I climbed on top of Atlas.



``What if--'' I started.  ``No.''



``Keep talking,'' Tattletale prodded me.



``What if I scouted the library, while you guys checked out the other site?  I can fly, it's faster for me to get there.''



``And we'd be one mistake away from you being killed,'' Grue said.  ``If not worse.''



``Hear me out.  Their only real long-range attacker is Jack, right?  If I'm flying, the others won't be able to touch me.''



``You think.''



``I think.  But if Jack's at the location, I'd be able to sense him before he got a bead on me.  If that's the case\ldots I can just attack without exposing myself, and I can alert you guys.''



``Assuming he's not two steps ahead of us and waiting at some vantage point somewhere nearby,'' Grue said.



``He functions like a sniper,'' Tattletale said.  ``Ignore the fact that he slashes and stabs, he's a long-range combatant with a good sense of what the enemy is doing and how his teammates move on the battlefield.  He stays out of the way and makes surgical strikes, then relocates to another vantage point.  The only thing that keeps him from doing that all the time is how he has to stay involved with his team and keep them under control.  Can't make it look like you're in charge if you're not there.  With less teammates to manage, he's liable to go on the offensive.''



``But I have the ability to find him,'' I pointed out.  ``Before he finds me.  Amy gave me bugs that increase my range.  I'll be taking on some risk, but it means we're able to check both locations at the same time and keep an eye out for the Nine.  It's the best way to strike the balance we need.''



``The balance,'' Grue said.  He was clearly unimpressed.



``Minimal risk to maximum effect.  Your group will be safe because you're all together and you'll vastly outnumber them.  I'll be safe because I'm airborne, and I'll have the advantage of an early warning.  Offensively, you guys will have the Travelers and Bitch.  I'll have my bugs.''



``Bonesaw countered your bugs last time around,'' Tattletale pointed out.



I nodded.  ``I have a few things in mind.''



``If you're sure.''



``She's not the only person who gets a say,'' Grue said.



``Name a better option, then?'' I said.



``We all go to the library's shelter, then we all go to the shelter Leviathan attacked,'' he said.  ``Safer, smarter.''



``If you're worried about me being defenseless,'' I suggested, ``Regent could come with me.''



``There's a reason we're keeping that pair close to us,'' Grue said.  ``If he gets taken down, you'll have to deal with Shatterbird on top of everything else.  We're capable of handling her, I think.  I don't know if you are.''



I frowned.



Tattletale looked back at the others, then back at me.  ``Go.''



I looked at Grue.



Tattletale pointed.  ``Go!  Stay in contact!''



I turned and lifted off.



I kept to the cover of nearby buildings, and I flew erratically, so Jack wouldn't be able to hit me if he saw me coming.  I was getting more used to flying Atlas.  I wouldn't have said he felt like an extension of my own body in the same manner as my swarm.  He felt more like a prosthetic limb, or how I imagined a prosthetic limb might feel like.  At first, it would be clumsy, every action requiring some level of careful thought and attention.  Over time, it would become more second nature, a learned skill on my end.  It would never match up to the real thing, but I could deal.



Already, I was getting more used to correcting orientation and keeping him level in the air.



We set down on a rooftop a distance away.  There was a shed with a doorway that led into the building's interior, and we headed there to take cover.



I chained relay bugs together so one connected to the next, then extended them well beyond the range of my power.  Their progress was relatively slow, but it did allow me to sweep over an entire region around the library.  Bugs stirred into action at my order, and they crawled or flew within a few feet of every horizontal surface that Jack or Bonesaw could be standing on.



No sign of them.  The vault door beneath the library was closed and sealed.



I was about to return to the others when an explosion of dust and rock fragments ripped through a group of bugs a few blocks away from me.



A woman, no clothes.  My bugs slid off her skin.  Even the slightest abrasion on the surface of the skin served to tear through the legs and bodies of the bugs.  Had to be Siberian.  If the general shape of the large object she was holding was any indication, she still held the truck.



A handful of my bugs were wiped from existence a fraction of a second before more explosions of varying size ripped through the area around her.  Legend was somewhere up in the air.



I drew my bugs together around Siberian's head, in the hopes that I could distract her.  It was pretty thin, but there wasn't much I could do.  Even a direct hit with Legend's lasers wouldn't affect her.



I shifted locations, flying half a block before landing again.  I could just barely make out the pair of combatants with my swarm sense.



Something about what Legend was doing seemed odd.  He wasn't firing constantly.  Rather, his shots seemed to be strategically placed.  He ripped apart the side of a building a moment before Siberian landed there, then tore through the five or six floors beneath her so she had nowhere to go except straight down.  The instant she stepped free of the building's ground floor, he tore into the ground with a series of laser blasts that expanded outward, thinning as they went.  It created a bowl-shaped indent, with rubble covering the storm drains that had been exposed by the lasers.



Carrying the truck, Siberian headed for the storm drains anyways, tearing through the piles of debris.  Legend unloaded on the entire street, collapsing them around her.  Some of my bugs descended with the pieces of the shattered street, and they could feel the warmth of the outside air mingling with the cold, stagnant air of the storm drains.  He'd exposed her.



I'd seen Legend go all out, and this wasn't it.  Why was he holding back?  Granted, there was little point in hitting Siberian with everything he had, and it was easily possible that trying to drill a hole in the ground around her could theoretically give her the chance to escape, if she found some underground cavern or tunnel, but it could just as easily drown her.  So long as she had the truck, Siberian had to stay places where there was oxygen.  She couldn't, I was assuming, dive beneath the water and make her escape from there.  Legend seemed to be going out of his way to keep her aboveground and exposed, attacking only when he had to.



\emph{He was conserving his strength}.  As much as both he and Siberian were powerhouses with more offensive capability than ninety-nine percent of people on the planet, this was a strategic battle.  It was easily possible he was planning to keep this up for hours, harrying her, keeping her from getting her feet under her.



And with Siberian's master or controller in that truck, she was forced to move more carefully.  If Siberian's creator didn't have food and water, this could turn into a battle of attrition.  One Legend might even win.  He was fit, healthy, athletic.  Siberian's master, according to Cherish, wasn't.  Added to that, being in that truck as Siberian leaped around couldn't be fun.



I felt like I was still missing something.  Why was Legend fighting \emph{here}, of all places?  Whatever else was going on, they were causing pretty horrific property damage, and it had to be hard to fight Siberian in a place with this many high-rises.  She could disappear into building interiors, and even if he lowered the height he was flying at, Legend was probably having to penetrate three or four stories of building to get to her.



I kept my distance from the fight as I directed Atlas toward the library.  With my bugs, I was able to more or less follow the fight.  I couldn't touch Siberian directly, but I could sense where Legend was directing his attacks, and how he was positioning himself.



I continued to do what I could to help Legend, sending bugs at Siberian in the hopes of distracting her or finding some way into that truck.  They searched the windows but failed to find a gap.  Some crawled into the exhaust, others into the undercarriage-



She fell into a trench as Legend leveled another series of blasts at her, and the movement of the truck coupled with Siberian's power and its rough texture murdered a solid ninety-percent of the bugs I'd used.  The remainder made their way deeper inside.



The bugs could scent something they registered as food.  A heavy smell, fetid, like garbage.  It was rank in there.  They crawled through the air conditioning vents and into the truck's interior.



The driver's seat was empty.  I sent the bugs into the back.  Nothing.



The truck was empty?



With my bugs, I drew out words in mid-air high above me, informing Legend: `TRUCK EMPTY – SIBERIAN BLUFF.'



Had she assessed what Legend was doing, turned it around on him?  If her real self was somewhere safe, somewhere with food and water, that meant Legend would lose any battle of attrition, if that's what he was aiming for.



I couldn't think of another reason her creator would leave the safety of the truck.



Hovering over the library, I got my phone out and dialed.



``Tattletale?''



``Sup?''



``Legend's fighting Siberian here, but the maker isn't in the truck.  I think he's in the vault with Jack and Bonesaw.''



``Someone's sealed over this door with a heavy pad of metal, because Leviathan or someone tore it down.  My gut's telling me the Nine didn't gather inside and weld it shut behind them, but I can't ignore the possibility that Bonesaw's spiders did it.  One in twenty chance, I'd guess?  We'll know in about thirty seconds, after Sundancer burns through.''



``Right.  A few more things that are bugging me.  Can I use your brain?''



``Go ahead.''



``Legend's fighting Siberian \emph{here}.  It feels wrong.  He's working to pin her down, slow her movements as much as he can.  I know he's probably buying time, trying to wear her other self out, but why not a place with flatter terrain?  Why not a place where there'll be less cover for her and less collateral damage?  I know Siberian goes where she wants, and if her other self is in the shelter, that's probably a big reason she came, but--''



``Your gut is saying something's off.''



``My gut is saying something's off.''



``Okay.  I'd guess the Protectorate have more of a plan than the one firebombing.''



``They're going to do it again?''



``No.  The first one, going by what you've said and what I've picked up, hasn't done much for our side.  It's going to be something else.''



``And we don't know what?''



``No clue.  What else?''



``Minor, but if her other self is in the shelter, where are Jack and Bonesaw?  And if \emph{they're }in the shelter, where's Siberian's real body?''



``She's spent years with them, they have a rapport, and they're dependent on one another. Maybe he felt it was safe to approach them.''



``Maybe.  Nothing more specific?''



``Don't have much to work with.  What else is going on?''



``Legend's holding back.  Conserving his strength.  I get that he's trying to win a fight of attrition, but as far as I can tell, he hasn't changed his tactics or the pacing of his attacks much since I informed him that the creator isn't in the truck.''



``He's buying time for something?  Someone?  Maybe Scion is headed this way?  No.  Don't get that vibe.  Hmm,'' Tattletale mused.  ``We just got inside.  They aren't here.''



I looked down at the library.  ``Vault door, how do I open it?''



``Can't say until I see the control panel myself.  The shelters are supposed to open with a command from the PHQ--''



``Which was annihilated,'' I said.



``Right.  Or the PRT headquarters, on the Director's order.  There's bound to be another code that can be used in case those places get knocked out of commission.''



``How did \emph{they} get in?''



``They have a tinker,'' Tattletale said.  ``She may work primarily with biology, but that's not going to be the full extent of Bonesaw's knowledge.  Look at those spiders.  Some basic hacking isn't out of the question.  Anyways, I can figure it out when I get there.  Unless you want to take the brute force route.''



I looked down at Atlas.  ``I don't have enough brute force, and neither does Atlas.''



``\emph{Legend} does.  We're on our way.  See you in a few.''



``Right.''



I hung up.



I drew more words in the air with my bugs, near Legend.



`FOUND THE 9.  UNDERGROUND SHELTER.'



As an afterthought, I added:



`MAYBE CIVILIANS INSIDE.'



I drew an arrow by the words.  Then, to make it as clear as possible, I drew a giant arrow in the sky, pointing down at the shelter door.



I was going to look foolish if they weren't inside, and maybe cost Legend in whatever plan he was operating under.



I could feel him changing directions.  He kept facing Siberian, unloading laser blasts, but he was flying my way.



Siberian dashed forward.  I could feel her cutting a swath through the swarm as she ran, the truck in one hand, one corner of it dragging on the ground, cutting a line into the pavement.  She leaped into the air, out of the reach of my swarm-sense.  I felt something massive collide with the bugs that were in the air around Legend, felt more die as he shot a laser and caught them in the area.



She'd thrown the truck, and he'd obliterated it.



Legend shifted into high gear, flying out of reach of Siberian as she lunged for him.  He dove, hard, and I could imagine her leaping off the side of a second building, trying to get her hands on him.



Legend turned my way and flew towards the library.  I hurried out of the way, directing Atlas to higher altitude, just in case Legend decided to level the place.



The leader of the Protectorate had arrived on the scene, and I could sense Siberian on the ground, hot on his heels.  He raised one hand, and a laser beam shot forth, splitting into eight smaller beams that bent in the air.  They hit the outside edge of the vault door with precision, evenly spaced out, then drifted in a clockwise direction.  The door toppled free.



Legend spread his arms, and \emph{hundreds} of individual beams radiated out from his body.  Three quarters of them turned in sync to spear towards the library, stabbing through the architecture.  Other beams split off to strike through doorways and windows and across rooftops.  No less than three struck \emph{me}.



I flinched and nearly lost my seat on Atlas, but found it wasn't much hotter than steaming tap water, and it only lasted two or three seconds before cutting out.  Siberian had approached close enough to demand Legend's attention, and he'd terminated whatever it was he'd been doing.



I turned my mind away from whatever the beams had been intended to do and toward my own contributions to this fight.   Had to strike before they got their bearings.  I took advantage of the pause to send bugs flowing into the shelter.



I could count a number of people, young and old.  The mosquitoes in my swarm could scent blood.  Twenty or so people were inside the shelter, standing there.  There was metal on their bodies, like backpacks or prosthetic body parts, but they didn't seem to be hurt.



There were three more inside, but I wasn't feeling so generous as to call them `people'.  They stood apart: two men and a preadolescent girl.



It was them.  The Nine.



I couldn't trust my ability to get to Legend and communicate the necessary details in time, and I might even be endangering him by getting too close to Siberian.  I couldn't say for sure how he would really act in the field, but his PR sold the idea of a legitimate good guy who would balk at attacking an enemy with a hostage.



Or maybe he wouldn't.  It could even be a mercy, sparing someone from one of the Nine's clutches.  Siberian devoured people alive.



Either way, it was better to try to catch his attention with a written message: '20 CIVILIAN, JS, BS, SIB'.



He was too distracted by Siberian to see it.  She wasn't as fast as Battery or Velocity, but she had the physical power to move quickly, and she was leaping between buildings to throw herself at him with the speed and aim of an arrow shot from a bow.



I tried leaving another message for Legend, stating the same thing.  Glancing over my shoulder, I saw him looking at me.  Our eyes met.  He nodded, and I turned my attention to the shelter.



I didn't want to do this half-assed.  No mistakes this time around.  I gathered a swarm of generous size, but I held it at bay.  There were more preparations to carry out.  I drew the capsaicin bugs from beneath my armor and added them to the swarm.  I drew out silk threads and held them suspended in the air, ready for use.  For a final measure, I withdrew a lighter and the changepurse from the utility compartment at my back.



Primary swarm in first.  As one singular mass, they flowed inside.  The capsaicin-laced bugs joined them, going straight for the eyes.



Jack reacted, as did the man, but Bonesaw was unfazed.  I saw Siberian flicker.  Legend noticed as well.  He snapped his eyes to me, and then the shelter.



\emph{The creator needs to concentrate?}



My heart was pounding so hard I felt like it would dislodge me from Altas.  Bugs settled on the three members of the Nine and then they attacked.  It wasn't the sort of attack I'd ever done before.  I'd had bugs bite, I'd had them sting, I'd even used them to deliver payloads of their various venoms.



I'd always held back to some degree.  The only ones I hadn't held back against had been untouchable.  These three weren't so lucky.



Mandibles bit into flesh, seeking not to pinch and inflict pain.  Ants scissored flesh away, beetles tore and rent into the flesh, flies spat their digestive enzymes onto the exposed flesh.



I buried them in every kind of insect I had that could eat, cut or pierce meat.  The bugs didn't eat their fill: they simply bit, chewed, let the food fall from their mouths, then bit again.



Bonesaw's hands were smooth as glass as she reached for her belt.  She was cool and collected, even as the bugs slowly flayed her.



She was stopped short as the silk strands tangled her ceramic fingers.



My bugs could hear her speak.  Though I could barely make out the words, I thought maybe the first one was `Jack'.  She held out her hands.



I tried to bind him, but tying his arm to his side was harder than using silk cords to lash fingers together.  At least partially blinded by the capsaicin, he swiped his knife a few times in Bonesaw's direction.  He cut her several times, and my bugs could feel her flesh part around her collarbone and face.  Some of the cuts were on target, however, and the threads around her fingers were severed.  An instant later, she was free to put together her anti-bug smoke, working her hands to break the threads as I tried to tangle her fingers again.



Okay.  Not the end of the world.  The bugs were still devouring the three, and I still had a plan in mind.  An idle hope.



I withdrew the tissues I'd wadded in the changepurse to keep the contents from jingling or rattling around.  My bugs took hold of them and carried them into the air, two or three dozen in all.



I tested the lighter, then held it out to ignite the first tissue.



It was a slow burn, taking fifteen or twenty seconds to consume the paper.  The flies that carried it died as the flame reached them, consuming them.



By the time the first was burned, my bugs were positioning the second, allowing it to ignite.  In this manner, I chained them one after the other.  A slow-moving relay of flame.



Bonesaw had her smoke going, despite my efforts to rebind her fingers, and I could feel it murdering my bugs en-masse.  I pulled them away and out of the shelter, leaving only a few to track the movements of the Nine.



The trail of burning tissues made their way inside the shelter.  I ignited the last few tissues and sent them to Bonesaw.  I could feel the bugs die as they hit the smoke.



Nothing.  I swore.



It had been too much to hope for, that the smoke was flammable.  Even if the smoke had exploded in the mildest possible way, it would have at least given me a countermeasure.



I turned away from the area.  I'd told the others I would play safe.  I'd tried what I could, I'd maybe even done a little damage to them, now I'd back off.  I'd earned Siberian's attention by attacking her creator, but she was preoccupied with Legend, so that was one threat I didn't have to worry about.  The rest of the Nine were still inside.



Legend, for his part, was keeping up the measured, carefully paced assault.  I saw him raise one hand to his ear.



A communication from his team?  Had something happened with the rest of the Protectorate?  Or the other members of the Nine?



He dove straight for the shelter.  Siberian gave chase, and without slowing in the slightest, he raked a laser across the street to render her footing less stable.  It couldn't have bought him more than a fraction of a second, if it even made a difference at all;  I could see her placing one foot on a shattered piece of road that wouldn't have held a squirrel without collapsing.  She used it to kick herself forward, soaring after Legend, hands curled into claws.  He was ahead of her by only ten or fifteen feet.



The scattered bugs I had at the fringes of the extermination smoke gave me only a half-completed picture.  Legend inside, blasting a laser in the direction of the cloud where Jack, Bonesaw and Siberian's creator were.  He grabbed one of the civilians that were standing dumbly in the shelter, only to get mobbed.  She latched onto him, and the others did the same, trying to drag him down.  My bugs felt a flash of heat as he used his laser to blast at them and free himself.  Another laser speared out of the top of the Library, followed soon after by Legend, spearing up toward the sky.  He directed another laser straight down at the library, continuing to fly straight up.



That was reason for me to do the same.  I rose with one hand on Atlas' horn, and I drew my phone with the other.  I speed dialed Tattletale.  Trusting to her penchant for picking up the phone on the first ring, I started shouting before I heard any response, ``Something's up!  Take cover and get back!''



The stealth bomber streaked across the sky, just as it had before.  Its payload this time was smaller, barely visible.



The devastation wasn't so easy to miss.



The only word for it was chaos.  I could hardly pick out the individual effects as they mingled.  A cloud of yellow-green smoke being pulled into a spiral around a vortex, which was causing the section of the library that had turned to glass to shatter and implode.  There was a flare of brilliant mixed colors I could barely look at, frying a scattered assortment of boneless, faceless, fleshy monsters.  One monster made it four steps before being turned to dust.  Where the dust touched, more dust was created, until the vortex expanded enough to start pulling it all in, stopping what might have been an endless chain reaction.



I could see time slowing in one spot, I could see pavement heating into a liquid in another.  I could see one area that was serene, untouched, a bubble where a newspaper that had been scattered on the ground was flapping violently with the movement of air.  Half a building was annihilated by the flash of an explosion, and it toppled into the midst of the bomb site.  In seconds, it was obliterated and chewed up.



The effects spread and expanded all down the street, a stripe of this madness three blocks wide, extending into the midst of the blaze from the previous bombing run.



I drifted toward Legend, raising my hands over my head to show I meant no harm.



``Thank you for the assistance,'' he spoke, when I was in earshot.  ``Some was misguided or off target, but it did make a difference.''



I could only nod.



He put one hand to his ear, then paused for several long seconds.  When he spoke, it was vague.  ``Acknowledged.''



I waited, staring down at the disaster area below.



``Crawler and Mannequin observed to be in the blast site.''



``How did they disengage while keeping them there?  They- they did disengage?''



``Clockblocker managed to tether Mannequin in place.  Crawler freed himself from the same trap by tearing himself in two against the immovable object.  It was Piggot who managed to keep Crawler in the blast area.''



``How?''



``She had Weld pass on a message, telling Crawler what we had planned.  He was so tickled at the idea that we would be able to hurt him that he stayed where he was while the teams made their retreat.''



``Just like that?''



``Apparently so.''



``If he survives--''



``He didn't.''



There was a series of smaller explosions below.  I could see a section of ruined building glowing red, then detonating in a blast of light that sent a nearby glacier spinning into a patch of burning ground.



``And the other three?''



``Remains to be seen.  The civilians are dead, but it's something of a mercy.  Bonesaw's mechanical spiders were welded to their skeletons, allowing her to remotely control them.  Like zombies, only they were aware and in incredible pain.  I expect she had measures to inflict agonizing deaths on them if we attempted to disconnect them from her spider-frames.  Maybe I could have saved them, can't say.  From the glimpses I saw of them, I don't know if they would have thanked me.''



We spent a minute staring down at the devastation.



I ventured to ask him a question, ``Can Brockton Bay take this?  It feels like it was on the verge of collapse already.  Add this mess, the firebombing\ldots can we really come back from it?''



``You know this city better than I do, I'm sure.  I like to think people are stronger than they appear at first glance.  Perhaps the same goes for cities as well?''



``I'd like to think so.  But if I'm being realistic--''



I stopped mid-sentence.



My bugs had found a group of individuals on the edge of the blast radius.



``No fucking way.''  I pointed.



Siberian flickered violently as she crouched beside Jack and Bonesaw, one hand on each.  In between the three of them was a man, hunched over.



Legend raised one hand, but he didn't shoot.



``Legend?''



``They haven't seen us.  I would like to take out Jack or Bonesaw while they're distracted and unguarded, I just need Siberian to step away or let go of them.''



The group shifted positions, so the man had an arm around Jack's chest and an arm around Bonesaw's shoulders, Siberian behind him.



``See that?'' Legend asked.



``What?''  I could barely make them out from our vantage point.  ``I can't.''



``My eyes are better than most.  A minor benefit of my powers.  The backs of his hands, perhaps you can make out the tattoos?  A cauldron on the left hand, a swan on the right.''



``I- I don't follow.''



``No,'' he sighed a little.  ``I suppose you wouldn't.  It does mean we know who he is.''



``Someone I'd know?  An old costume?''



He shook his head.  ``A scholar.''



Jack glanced up, and Legend fired in the same instant.  With Siberian's strength, the group  of the Nine lunged to one side, disappearing behind cover.  I sent bugs after them.



My swarm sensed other arrivals.  The Undersiders and Travelers came from the west, taking a circuitous route around the top end of the bomb site.  Legend fired a series of blasts after Siberian and gave chase, but she was keeping a building between her group and Legend.   He stopped where he was, one hand outstretched, and touched his ear.



``My teams are on their way,'' he said.



``That's good,'' I said.  ``The Undersiders and Travelers are too.  I'm going to go fill them--''



``We need them to back off,'' he interrupted.



``Another bombing?''  I asked.



He shook his head.  ``No.  It seems we're facing the worst case scenario.''



``We're \emph{winning,}'' I said, incredulous.  ``You guys took out two of them, we've got them on the defensive--''



``Exactly,'' he interrupted me.  ``We're winning.  And we've broken enough of Jack's rules for his `game'.  Now I fear we're about to see whatever `punishment' it was that Bonesaw prepared for us.''





