





``How did it go!?''  Tattletale called out to me before I'd even landed.



I set Atlas down on the ground and hopped off.  ``Whatever the fuck they just dropped on the city, it apparently took out Crawler and Mannequin.''



``I'll believe it when I see it,'' Tattletale said.  ``I think that was Bakuda's stuff they just used.  What about the other members of the Nine?''



``They're on the run.  Last I saw, Siberian's creator looked pretty rough.  Not sure if the spider bites and stings will kill him or if Bonesaw will manage to counteract it.  Depends on whether Legend and the other heroes can keep up the assault long enough to keep Bonesaw from getting to work.''



I could see Bitch react to the mention of Siberian's creator.  She looked startled, then scowled.



``You found them?''  Tattletale asked.  ``Siberian and Legend?''



``Yeah.  Legend told me to scram, in case Bonesaw deploys the threat she's been holding over our heads, and so I don't get in the way.  I would have fought to stay, but he's an intimidating guy to argue with.''



Grue nodded.  ``I wouldn't feel bad about it.  It means we can serve as backup if the heroes lose.''



``And this threat?  Do we know what it is?  Some zombie apocalypse?''  Regent asked.



``No.'' Tattletale shook her head.  ``She sees herself as an artist.  She's going to want to do something that catches us off guard, something that scares us in a way that simple horror movie monsters don't.''



``I don't know about you guys,'' Sundancer spoke up, ``But monsters scare me enough.''



``Says the girl who can vaporize buildings and give Leviathan pause for thought,'' Regent said, giving her a sidelong glance.



``Leviathan broke half the bones in my body.  The only reason I'm standing here is Panacea,'' Sundancer said, a little defensively.



``You two do raise a point, though,'' Tattletale cut in.  ``Capes are powerful.  If she wanted to scare the locals, she's done that.  I'd be willing to bet the ace she has up her sleeve is going to be more aimed at scaring people like \emph{us}, like Legend.  She wants to terrorize the strongest, target people who everyone looks up to and fears.''



``\emph{Just} us?'' I asked.



``She's shown she knows how to disable powers,'' Trickster said.  ``If she did that on a larger scale, then--''



``No,'' Tattletale shook her head.  ``She wouldn't have used the dust and the darts if that was the big reveal.  It doesn't make sense tactically, because we could have come up with a way to deal, and Skitter's partially immune anyways.  And it doesn't make sense artistically, either.  You have to think of her as less of a scientist or doctor and more of a performer.''



A thirty story skyscraper tipped over and crashed to the ground in the distance.  The rumbling crash of the building's collapse seemed delayed in getting to us.  I could see Legend, more through the flashes of his lasers than anything else, but everyone else was out of sight, specks I couldn't have made out if they weren't on the ground.



``If we're lucky, we won't have to worry about Bonesaw's plot,'' Trickster said.



``Plan for the worst,'' Grue replied, staring into the distance, ``If you're right, you're prepared.  If you're wrong, you're pleasantly surprised.''



``Heard that one before,'' Imp commented.



``Still true,'' Grue replied, sounding annoyed.



``Can't plan for this,'' I said.  ``I'm growing to hate tinkers.  People with enhanced senses and tinkers.  And fire manipulators.  Sorry, Sundancer.''



She shrugged.



I turned back to the subject at hand, ``We can't guess what she's come up with because her tinker abilities make her so versatile, and that means we can't preemptively set up any countermeasures.''



Tattletale tucked her hair behind her ear.  ``Fits in a vial, assuming that vial she was showing off was the real weapon, something to do with water, she said\ldots you guys haven't been drinking anything except bottled water?''



There were head shakes and the occasional muttered ``No'' from the rest of the group.



``I've even been making my tea with it,'' I said.



``And we know there's going to be a strategic purpose behind it, beyond causing terror,'' Tattletale went on.



``You're getting into that headspace again, Tattletale,'' Grue said.  ``Tunnel vision.''



``Right.  I'm done now,'' Tattletale replied.



``Is it such a problem?'' Trickster leaned forward, ``If you can give us answers about this thing, that's good, right?''



Tattletale shook her head, ``If I'm digging deep enough for answers that I'm losing sight of other things, it means I'm probably speculating, and that tends to mean I'm generating false positives, heading down the wrong path to the wrong conclusions.  I told Grue to stop me if I'm doing it, and Skitter's right when she says we can't anticipate what Bonesaw's going to do, so it's pointless anyways.''



``If we did want to take countermeasures,'' I said, ``We should maybe think about tracking down Amy.  Or figuring out where she is.''



``Panacea?''  Grue frowned.  ``She didn't exactly leave us on good terms.''



``I know.  But she can counteract whatever Bonesaw does.''



``Unless she falls victim to it,'' Tattletale said, sighing.  ``After two bad incidents downtown, I'd lay odds she's heading up toward the docks.  It gives her the best odds of finding a place that's empty, where she and Glory Girl can hide out for--''



``Heads up!''



I wasn't sure who had shouted the warning, but I turned to look in the direction of the fighting, and I instantly knew it was Bonesaw's work.



The water was turning crimson.  Where it was only one or two inches deep above the pavement, it turned a dark red that resembled blood.  That alone might have been spooky enough, but it was spreading over hundreds of feet in a matter of seconds, and there was a thin red mist rising in its wake.



``Run!''  Grue shouted.



I was on top of Atlas in an instant, and in the air a second later.



``How is it spreading so fast!?''  I asked, while the others seated themselves on the two dogs.



``She must have set it up beforehand!''  Tattletale called out.  ``Just needed the catalyst!''



She checked to make sure Trickster and Sundancer were seated and had Bentley at an all out run a heartbeat later.  Sirius followed just two steps behind, carrying Grue, Imp, Bitch and Ballistic.  Regent joined me in the air, hanging in a less than dignified way from Shatterbird's embrace.



I needed only one glance to know they weren't running fast enough.



``Sundancer!''  I shouted.  ``Cut it off!''



It took her three or four seconds to pull an orb together, no larger than a basketball.  It grew to twice the size as it flew, raking across the street to turn the pooled water into clouds of steam.  I rose higher in the air to avoid being caught by the plumes of hot water.  The steam turned from a clean white to pink and eventually red as the effect reached it.



Sundancer's miniature sun had slowed the progression down our flooded street, but it wasn't enough.  From my perspective, I could see the water on adjacent streets undergoing the same transformation, moving forward until it was adjacent to the others, then extending forward.  It was a matter of time before it reached far enough forward that it passed through the side alleys and cut them off.



``Get to high ground!''  I shouted.



Bentley leaped for the side of a building in an alleyway, scrabbled for a hold, then leaped to the building face behind him, attempting the zig-zag movement that the dogs had done so many times before.



Except he wasn't as agile as the other dogs, and I suspected he wasn't as practiced at it as Brutus, Judas and Angelica had been.  Added to that, he was carrying a heavy burden.  One of his paws went through a window, he slipped, dug his claws into the wall and shifted to climbing the wall instead.



It was too slow.  The water turned crimson beneath him, and then the vapor began to rise, faster than Bentley was climbing.



``Tattletale,'' I breathed.



I massed thick clusters of bugs between them and the vapor, while Regent and Shatterbird followed Sirius and the others.



It was enough to buy them time, but that meant precious little.  No matter how much I pressed the bugs together into an airborne barrier, the vapor made its way through.  Worse, the mist was rising to either side of them, approaching the top of the building.



They reached the rooftop and Bentley heaved himself over the edge.  They hopped off his back as they reached solid ground, and Tattletale stepped over to the corner of the roof to watch the rise of the red vapor.  It was only a floor beneath them.



Trickster pointed at the top of a building nearby, then looked up at me.



I gathered my bugs there, again, pressing them together.  Trickster looked increasingly impatient as the bugs massed, and the vapor reached the edges of the roof.



I hurried over to the building, instead, then hopped off, sending Atlas over to the other rooftop.  Trickster swapped me with Tattletale, and I hopped over to ferry myself to the roof again.



Didn't trust my ability to use Atlas to carry someone else, when I had to struggle to process his sensory inputs.  Add someone else's shifting weight and movements, and I wasn't sure I wouldn't drop them.



I was on the building again when Trickster swapped me for Sundancer.  It left him, myself and Bentley standing on the rooftop.



I was on top of Atlas a second later, flying.  The red mist crept in from the outside edges of the rooftop.  He got on top of Bentley, looking less than comfortable holding the reins, and Tattletale whistled.  It wasn't as good as Bitch's whistles, but Bentley perked up and ran, leaping for the side of a nearby building.



He and Trickster reached the second rooftop quickly enough.  The mist was still rising, not just below us, but up around buildings nearly as far as the eye could see.



``Shit,''  Tattletale said.  ``Not good.''



``There's a taller building over there,'' I pointed.  ``We should head there before the mist gets up here.''



``I'd call it miasma,'' Tattletale said.  ``And is there really any point?''



``It might stop rising,'' I protested.



``It won't.''



``Is that an educated guess or--''



``It's not.''



I found myself at a loss for words.



``What does it do?''  I asked.  ``Poison?  Something else?''



``Probably something else.  Or it's poison, but it's designed to do something besides kill us.  How are the others doing?''



I looked for Grue and Regent using my swarm sense.  Grue, Bitch, Ballistic and Sirius were on a rooftop lower than us, Regent directly above them.  Cursory exploration with my bugs revealed a glass dome extending around the rooftop.  My bugs could fit through gaps in the glass, which meant the miasma would as well.  I did what I could to block up the holes, and I knew it was useless.



\emph{Brian}.  \emph{Rachel}.



``I think they're caught,'' I said.  ``I-I don't know what to do.''



``You have a gun.  You have your bugs.  If the Nine are going to let their guards down, it's going to be now.  All the ones who are still left are priority targets.  Finish off Siberian and taking Jack and Bonesaw out of action will be doable.''



``You're saying I should leave you.''



``Yeah.''  She looked down at the rising mist.



``No.  That's ridiculous.  Let's get you to higher ground.''



``It's futile.  You'd be buying us a little time, but this is looking pretty inevitable.  Your time is better spent going after the Nine.  If you can't find them, or if it's too dangerous, find \emph{Panacea}.''



``This isn't negotiable.  I- I can't do anything for Grue and Rachel and Ballistic, Regent tried and he failed.  Let me do this for you.''



Tattletale frowned.  ``Fine.  But you'll have to hurry.  That's a lot of distance to cover, and the miasma's nearly here.''



Trickster cut in, ``Gather bugs together like you were doing, remember that they're not as dense as our bodies are, so we need more than you'd think if I'm going to swap them for one of us.''



I nodded and flew for the tallest building in the area.  I turned around and waited for Trickster to swap me.



He didn't.  They stood at the roof's edge, looking my way, and the dark red miasma climbed up the sides of the building around them.



It felt like my heart dropped out of my chest.  Brian, Rachel, now Lisa?



I couldn't afford to turn around and confront them -time was too short- so I focused on gathering my bugs.  I clustered them together, pressing them into a largish human shape.  How many was enough?



I felt a jarring sensation as Trickster swapped my bugs to his location.  Sundancer appeared beside me.



``Why?''  I asked.



She shook her head, ``They didn't say anything.  They were both really quiet while you flew off, and then Tattletale said `It doesn't look like her plan will work out.  Tell her I'm sorry.'  Trickster teleported me here before I could say anything or ask what she meant.''



``Why isn't he telporting Tattletale out?  Or himself?  There's still time for\ldots''  I looked at the cloud.  Not enough time to save both, now.  ``He could save \emph{one} of them, and I could probably get Atlas there and get out of harm's way before the miasma reached me.''



``His power gets slower with distance and difference in mass,''  Sundancer hugged herself, ``Maybe it's too slow, and he doesn't think you'd have time to run.  Or--''



``Or.''  I said.  The sentence didn't deserve to be finished.  There was the \emph{other} reason.  The notion that he was deliberately avoiding using his power, because he \emph{knew} I didn't have the time to get back to them before the miasma reached them.  ``Are you going to be okay?''



``I don't know.  When you've left, I'll use my power, and I guess I'll wait here until--''  she stopped.



Until when?  There was nothing saying this miasma of Bonesaw's would disappear or settle anytime soon.



``I hate being alone,'' Sundancer said.  She settled into a sitting position.  ``It's like, I can count on one hand the number of times I've actually been on my own.  When I was little, I was always with my mom, or always in school, always in afterschool activities.  Ballet, violin, lyrical dance, voice lessons, acting lessons\ldots never a moment to think for myself.  Even after I stopped all that, I was with my friends.  Always in a group.''



I stared at Tattletale and Trickster.  I couldn't make out their faces, but my bugs could make out the shapes of sounds that had to be words.  They were having a conversation, just like we were.



``I remember you said it was lonely, being in the Travelers.''



``It was.  It is.  But I was still with them.  Part of the group.  The time I've spent in my territory is the longest I've spent on my own.  Actually managing the territory, scaring off Hookwolf's people, that was easy.  Being all on my own was unfamiliar ground.  Soul crushing.  I wound up going back to Coil's base and spending time with Noelle and Oliver.  But being alone, agonizing over everything that's been going on, no distractions\ldots''



The miasma had reached the rooftop where Tattletale and Trickster stood.  Trickster was pacing, while Tattletale stood with her back to me, her hand rubbing Bentley's blunted snout.



It took only a few seconds for the mist to close in around them.  There was no immediate reaction.  The two teenagers and the dog simply stood, silhouettes in a stirring cloud of vapor that ranged from ruby-red to crimson in shade.



I swallowed past the growing lump in my throat.



``And now I'm alone,'' Sundancer said.  ``You're going to go after the Nine, and I'll wait here, all on my own, going crazy as I wait and watch and see just what happens to them.''



``If I've picked up on anything over the last few months of wearing a costume, it's that humans are stronger than you'd expect,'' I said.  It was as much to myself as to Sundancer.  ``We can endure a hell of a lot of punishment before we break, and even after we're broken, we tend to keep on going.  Could be physical punishment: getting stabbed, getting scarred, broken bones.  Could be mental: losing a loved one, being tortured, even the way I feel like breaking down and crying over the fact that just about every other member of my team is probably \emph{fucked, }but I'm holding myself together?  Humans can put up with a hell of a lot.''



``I don't think this is the right time for optimism,'' Sundancer said, bitter.



``Optimism?''  I shook my head.  ``No.  It's a double-edged sword.  If we weren't so resilient, so tenacious as a species, I don't think we'd be having this much trouble with Jack.  I don't think Mannequin or Siberian would even exist like they do now.  I'd almost call it pessimistic.  Almost.''



She didn't reply.



``Speaking of Jack and Siberian--'' I started.



``Go.''



I left, taking off and heading for the spot I'd left Legend.  Looking over my shoulder, I could see Sundancer creating her orb and bringing it down on top of herself.  As it had done back during our fight with Lung, it didn't burn the area directly around her.



And Tattletale and Trickster\ldots were still standing in the midst of the miasma.  They weren't reacting or doing anything, but they weren't signalling for me to come back, either, and they weren't hopping on top of Bentley to rejoin the action.



Something was up, I just had no idea what.



I consoled myself with the bittersweet idea that Bonesaw would want to draw this out.  It wouldn't be as simple as murdering my teammates.  It wasn't exactly \emph{reassuring}, especially when I thought back to what had happened to Brian, but it gave me hope that this wasn't the last time I'd see my teammates.  My \emph{friends}.



I rose higher as I approached the epicenter of the miasma.  It had continued to rise, and the place she'd used the catalyst was the place where the vapor had spread the most.  I could see how it was threaded through the streets like veins, surrounding buildings in a crimson embrace, spilling out into the ocean.



The water of the bay, I noticed, hadn't changed.  Was the salt killing whatever organisms she'd designed to spread this effect?



There were areas of high ground where the effect was diminished or gone.  There were hills here and there where the area hadn't flooded and miasma wasn't reaching so far into those spots.  Hopefully that meant the civilians wouldn't be so affected; the high ground where flooding wasn't an issue would also be the place where people congregated for shelter.



A series of bright flashes caught my attention.  Between the distance and the cloud of red vapor, I could only barely make him out, but the staccato lasers let me identify him as Legend.  He was fighting.



I sent my bugs down into the miasma, drawing them together into a swarm and placing them strategically, painting a mental picture of the area, the layout, and the positions of the combatants.



Just to be safe, I drew closer to a rooftop.  It wasn't safe to land, but I had hopes the building would offer me some cover against Jack.  I held the bulk of my swarm at bay, waiting for the moment I could assist Legend in fighting the Nine.



He wasn't fighting the Nine.



Legend was shooting at teammates.  He shouted something, but neither my ears nor my bugs were able to pick out the words.



\emph{Really} wished I could use my bugs to hear.



Had they gone berserk?  Rage?



No.  I could sense others hiding.  In fact, it seemed to be the primary concern of the people in the miasma.  Hiding, staying out of trouble, putting distance between themselves and the others.  Even Legend was pulling his punches.  His lasers were nonlethal, as far as I could see.



Paranoia?



Weld, who I identified by his lack of a costume and the metal growths on his shoulders, was standing with his back to a wall.  His hands were blunt weapons, and he was swinging them through the air to threaten anyone who approached.  A small figure who could only be Vista was backing away from two adults.  She got too close to Legend, and he fired a spray of laser blasts at her.  None hurt her or penetrated her costume, but she staggered and fell.



I could sense the ground bulge, spearing up in a pillar.  As the ground beneath them stretched in the pillar's vicinity, others staggered or got disoriented.  At the pillar's top, a roughed-up Vista bent the growth she'd created to place herself close to the rooftop and hopped down onto solid ground.  She coughed.



Okay, at least she wasn't someone who could kill me if this went the wrong way.  I called out, ``Vista!''



She whirled on the spot to look at me, then swiftly began backing away.



I raised my hands to show her I meant no harm, ``Hold on!  I'm safe!''



``That's just what \emph{they} would say!''  She retorted.



\emph{They?}



``Who?  The Nine?  In what universe would I be a member of the Nine?''



``Shut up!  Don't try to convince me!  Just\ldots just back off!  Leave me alone until all this stops!''



She was breathing so hard I could see her shoulders rising and falling through the protective suit she wore.



A thought struck me.\emph{  It was working through the suit}?  The mask had to have filters for smoke, why hadn't it worked against this miasma?



``I just want to help.''



``Leave!''



She used her power, extending the pillar she had used to ascend to the rooftop.  It missed me by a wide margin, but the threat was clear enough.



I regretted it the instant I did it, but I moved \emph{forward} to avoid any further movements from the shaft of asphalt.  If I was going to fall, I wanted to land on the roof, instead of the alleyway a dozen stories below.



``No!''  The word was as much a scream as anything else.  She extended the shaft well over my head and then pinched it off so the top part fell.



I'd seen her fight Leviathan, and she'd done the same thing then, if on a somewhat bigger scale.  I had Atlas carry me out of the way and watched the teardrop shaped piece of asphalt crash to the floor of the alley.



That, apparently, was enough to get Legend's attention.  He rose from the street level and surveyed the scene.  He'd taken off the hazmat-style mask and filter, and what little I could see of his expression was drawn.  His eyes were narrowed, a vein stood out on his forehead, and he furtively looked from Vista to me and back again.



``Legend,'' I started.  How was I supposed to address him when he was like this?  When I didn't even know what was going on with them?



Not that it mattered.  He raised one hand in my direction, and I veered away, taking evasive maneuvers.  It missed me by a foot, circled around and struck me off of Atlas before I could cancel out his momentum and change direction.



Legend had clearly set his lasers to `stun', but it still hurt.  Hitting the rooftop hurt more.  I could feel a piece of armor crack beneath my weight, hear my things spilling to the ground.



I coughed out half a lungful of air and involuntarily sucked in another breath to cough again.  It was humid, tasting slightly off, almost stagnant.



When I opened my eyes, I was seeing red, and not in the metaphorical sense.  I was in the midst of the miasma.



Still coughing, I struggled to my feet.  The back compartment of my armor had cracked as my weight had come down on the lip of the roof.  My weapons, the epipens, the cell phone and the changepurse lay on the ground.



``Stay down!''  the junior heroine screamed.



If I hadn't still been reeling from my fall, I might have been able to avoid it.  As it was, the section of rooftop behind me bulged up into a wall and then folded down over on top of me.  It bent to accommodate my shape rather than crush me, leaving only my head and shoulders sticking out.



``If you try that trick on me, little girl, I'll shoot you,'' I heard the threat from the air above us.



This was going south, fast.



``I'm going to turn my back and run,'' she responded.  ``If you try shooting me in the back, I'll show you what I can \emph{really} do.''



There was anger in the threat that caught me off guard.  Was it this miasma that had pushed her to that level of anger?  I wasn't feeling anything like that.  Had something about the way he had talked provoked her?  Or was that the norm for her?



I tried to think back to my prior experiences with her and found nothing.



What was her name?



Was I suffering from brain damage?  Another concussion?



I did a series of multiplication, addition and subtraction in my head and found no problems on that front.  Not general brain damage, apparently.



Amnesia?



\emph{My name is Skitter}, I thought, \emph{Taylor Anne Hebert.  Sixteen.  Born in Brockton Bay.  Student at Winslow High.  Ex-student.  Member of the Undersiders}.



No problems on that front.



My line of thought continued absently, as if I wanted to reassure myself that I was mentally intact.  \emph{My parents are}\emph{Dan Hebert and Annette Rose Hebert}.



I struggled, wiggling to try and free myself from the hump of solid concrete.  I could inch myself out.



\emph{What would my mom think to see me now?}



I tried to picture her expression.



Again, that gap, the chasm.  Nothing.



I could have been hit by five more of those laser blasts on `stun' and it wouldn't have hit me as hard as the realization that I couldn't remember my mother.  Couldn't remember her face, the details, her mannerisms.  Even the happy memories we'd shared, the little moments I'd clung to over the past two years, they were gone.  There was only an empty void where they should have been.



I couldn't remember my dad, either.



The other Undersiders, their faces, their costumes, their personalities and mannerisms, all gone.  I could remember what we'd \emph{done}: the bank robbery, fighting Purity's group, lazing around in the old loft, even the general progression of events from the moment I'd met them.  But the \emph{people} were blanks waiting to be filled in, and I couldn't go from thinking about one name to thinking about the events that were related to it.



I felt a rising panic as I struggled to work myself free.  I didn't know the people who were on the rooftop with me: the man who floated in the air, wearing a sturdy hazmat-style firesuit and a blue and silver mask that left only his mouth, chin and wavy brown hair exposed.  I couldn't recognize the girl he was shooting in the back.  I saw her fall face first and writhe with pain.  He shot her two more times, and she went limp.  Out cold.



I couldn't make the mental connection between \emph{the Nine} and their appearances or their powers.  If I didn't have the benefit of being able to remember my actions over the past few minutes, it would have been impossible to say whether the two people here were allies or enemies.



Everything suddenly made sense.  The infighting, the tactics they were using, the mixture of hostility and paranoia.  Legend was attacking with nonlethal blasts because he couldn't be sure if he was attacking a teammate or one of the Nine, so he was striving to take \emph{everyone} out of action with as little permanent damage as possible.



Sundancer's worries about being alone struck me.  We were all alone, now.  Every single one of us.  From teams to individuals, everyone was fending for themselves because they couldn't afford to trust the others.



And it would ruin us.



It would be impossible to mount any kind of defense against the Nine if we were fighting them as individuals.



The man with the blue and silver mask floated over to where I was, ready to dispatch me, to knock me out, just in case I was a threat.



``Help?''  I called out.  It was a spur of the moment response.  My mind raced as I tried to form a plan.  Even a bad one would serve.  I lied, ``I'm stuck.  Break me out?''



I stared up at him.  His face was riddled with conflicting emotions, his body language tense.  There was a nervousness there that belied simple amnesia.



We'd been warned about drinking the city's water.  It might mean the effects were more pronounced for the people who hadn't been informed.  Or there might be side effects.



``Stay,'' he ordered.



He stayed at the level of the rooftop as he floated out above the street, aiming more blasts at the others.



This wasn't rational for him, it didn't jibe with my knowledge of him.  That could mean there was something about the miasma that was making him \emph{irrational}.



I waited for long minutes as he continued firing down on the others.  He cast me one sidelong glance, then flew off in pursuit of someone I couldn't see.



Even after I was able to start wiggling myself free, it was slow.  I measured my progress in half-inches.  My chest, small as it was, proved an issue.  Coupled with the armor at my front and the remains of the armor at my back, it made getting free an issue.  Several times, I stopped breathing for a good minute before I forced myself back under the concrete sheet to be able to breathe again, then I did it again.  As much through the wear and tear on my armor as anything else, I managed to slide my upper body out on the fifth attempt.  I took a second to breathe and rest, and then began the slow process of getting my midsection and hips past the mouth of the concrete shelf.



I directed every curse word I knew at the belt and armor panels I'd placed around my hips as I tried to work myself free.  My hips and rear end were proving as difficult as my chest had been, and with my upper body being further away, I couldn't get the same leverage push myself out with my arms.  Minutes passed as I grunted and struggled.  I could hear inarticulate screams, shouted threats, screamed warnings and the noise of destruction on the street below as paranoia gave way to violence.  I brought Atlas to my side, but even with his strength and his horn, he wasn't strong enough to affect the concrete.  I used his help to squeeze myself out, bracing his horn against the lip of the concrete sheet and pulling.



When I was free, I gathered my knife, baton and gun from where they had fallen and fit them into the few remaining elastic loops in my ruined utility compartment.  Cell phone was a yes, but I didn't have a spot for it, so I tucked it in the chest compartment of my armor.  Similarly, I stuck the epipens and changepurse through the space between my hip and the belt, wedging them in next to the straps.



I double checked that Atlas hadn't been hurt by Legend's lasers and then climbed on top of him.



There was destruction below, and signs of the mad fighting between capes.  Sheets of paper frozen in time, a mailbox destroyed, a light-post toppled, all still in the midst of the red water.  Everyone had fled or been knocked out of commission.  The fighting had migrated to several scattered spots nearby.



I didn't know exactly what to do, so I focused on helping the wounded, making sure they were okay.  I turned an unconscious girl over into the recovery position, and started to drag a wounded man out of the middle of the road.  I stopped when he started struggling and fighting with me and just left him there.



I felt lost.  Was I helping the enemy when I was propping someone up to make sure they didn't choke on their own vomit or drown in a puddle?  If I used the plastic cuffs I had in the changepurse, would I be tying someone up, leaving them helpless against one of the Nine?



I checked my cell phone.  No service.



I was alone here.  Everyone in the world was a stranger.



Vibrations rocked the street.  I saw the wounded man stir in response.



A monster.  Bigger than a car, fangs, teeth, claws, and a thorny exterior.  It didn't act like it had seen me.



\emph{One of Bitch's dogs?  Or is it Crawler?}



If it was Crawler, and I acted like he was friendly, he'd tear me to shreds.  I could draw my gun to threaten him, defend myself\ldots except that wouldn't do a thing to slow Crawler down.



If it was one of Bitch's dogs sans rider, then there was little point in staying.  I didn't even know if it was suffering from the miasma's effect.  If it was Crawler\ldots



I drew my bugs around me as a shroud, simultaneously forming decoy swarms.  I ran, my footsteps splashing, and called Atlas to me.  The second I was out of sight, I climbed on top of him and took to the air once again.



Couldn't settle down, couldn't stop.  I had to treat everyone I met as an enemy.



I was beginning to see where the paranoia came in.



``Skitter!'' a voice called out.



I stopped.



A blond girl, waving at me.



I drew my gun and leveled it at her.



The smile dropped from her face.  She brought both hands to her mouth as she shouted, ``It's me!  Tattletale!''



I hesitated.



How tragic would it be if I shot my friend, so soon after I'd wanted to scream at the heroes for fighting among one another?



``How did you get here?''



``On the dog.  I don't remember its name, but it wasn't as affected as we were.  This effect is tailored for people.''



I looked in the direction of the creature I'd seen.  Had that been the dog they'd come on?



I drew closer, but I kept the gun aimed at her.  I glanced around.  ``Where are the others?''



``Most are hiding,'' she said.  ``My powers kind of let me work around this gas, I think.  I brought Grue, too.''



I looked around.  What she was saying \emph{felt} right, even if I couldn't remember her powers, specifically.  ``What is this?  Amnesia?''



``\emph{Agnosia}.  We haven't \emph{forgotten}.  Just\ldots can't use the knowledge we have.  Looking at the others, I think they're hallucinating.  If it's prions, like Bonesaw used with the power nullification darts, it fits.  Hallucinations would match with heavy prion exposure.''



``Prions?''



``They're small enough to pass through water filtration and gas masks.  Badly folded proteins that force other proteins into identical shapes, perpetuating the problem.  If she found a way to guide them, or specifically target the parts of the brain she wanted, she might get results like we're experiencing.  In a really bad case, it'd cause lesions in the brain and give you hallucinations.''



I looked around.  ``How long does it last?''



``Forever.  It's incurable and it's terminal.''



I swallowed.  ``But Panacea could fix it.''



She nodded, then smiled wide.  ``There's hope, right?''



``Right.''



She jerked her head to one side, then used one hand to brush the hair back out of her face.  ``Let's grab Grue and formulate a plan.''



She turned to leave, but I stayed where I was.  After three steps, she turned around.  ``What's wrong?''



I didn't lower the gun.  ``Sorry, a little paranoid.''



She frowned.  ``That's fair, but we're short on time.  If others are getting lesions on their brain, then that means they could die soon.  Seizures, violent mood swings, loss of motor control\ldots  Creutzfeldt-Jakob was a prion disease, but the progression here's faster.''



I shook my head.  ``Crews-what?''



``Neurological disorder caused by eating the meat of a cow infected with mad cow disease.  You get the prions in your head, and you slowly die while suffering personality changes, memory loss and vivid hallucinations.''



``And it's faster here.''



She nodded.  Her expression was solemn.  ``Hours instead of weeks.  And as people experience mood shifts with anger and fear, or if the hallucinations get worse--''



``The fighting among teammates will, too,'' I finished.  ``It could get ugly.''



``If we're going to save everyone, we need Amy.  For that, we need to ask Cherish.''



I shook my head.  ``Who?''



``Um.  You remember capturing a member of the Nine?''



Did I?  We'd ambushed them, walked away with captives, yes.  But we'd lost someone too.



``Yeah,'' I replied.



``And we confined one?''



I nodded.  This was working.  I could piece together the information.  We'd called that person on a phone, hadn't we?  ``Cell phones aren't working consistently.''



``Is it safe?'' a male voice asked.



``Sure.''



I stayed silent.



He stepped out from around the corner to stand by the blond girl.  ``This is Skitter?''



She nodded.  ``Skitter, this is Grue.''



I didn't recognize him any more than he recognized me.  I kept the gun trained on them.



``This is slowing us down.  What's it going to take to get you to trust me?'' she asked.



What would it take?



``The fight with Empire Eighty-Eight's mooks.  When I made the human-shaped tower of bugs for the first time, and they shot into it while I crouched inside\ldots''



She shook her head ``I don't remember that.''



How many people had I been with, then?  I would have said one, but I felt like someone else was involved.  Had they arrived late?  I could remember hurrying off.



She spread her arms wide.  ``I'm sorry.  I might not look like it, but it's affecting me too.  I'm just using my power to uncover the answers we need.''



I nodded.  That would have been reassuring if I could remember what her powers were, or if I could think of something about her I could quiz her on.  It was like two blind people playing hide and seek.



``Look, come here,'' she offered.



I hesitated.



``You can keep the gun.  I'll keep my hands above my head.  Grue, stand back.''



He stepped away and leaned against a wall, his arms folded.



I landed Atlas and stepped forward.



She got on her knees, and with her hands above her head, she walked through the flooded street on her knees until her forehead was pressed against the barrel of the gun.



``I trust you.  I know I'm a pain in the ass sometimes, I know we've had our ups and downs.  I know I've kept way too many secrets for someone who calls herself Tattletale\ldots'' She smiled. ``But I \emph{trust} you.  Now, even if you don't recognize me \emph{consciously}, what's your heart telling you?''



In truth?  It wasn't telling me much.  If I didn't think on it, if I just went with the vague impression I associated with the name Tattletale, the smile, the fountain of information\ldots



I backed away a step.  ``I don't think that's a good enough reason to trust you.''



``Darn it.  Um.  Let me think\ldots''



``Do you want to go ahead without her?'' the guy asked.



I turned to look at him.  The idea of being left alone here-



``Go somewhere safe,'' he suggested.



I frowned.



``If the Slaughterhouse Nine find Panacea first, or if things get much worse--''



``I want to help, really,'' I said.  ``But it's just that\ldots''



I trailed off.



``You want to help, but you're suspicious.  And you feel bad for being suspicious, because of everything we've been through, our close calls?'' he asked.



``Yeah,'' I said.  I was double checking everything he said against my own awareness.  Was he saying anything that indicated he knew something I couldn't?



``I know how scared and suspicious you feel because I feel the same way.  Except I\emph{ }trust Tattletale.''



``I do too,'' I said, ``And I'd trust \emph{her} if I could be sure she was Tattletale.''



``Trust your heart.''



I wanted so desperately for it to be like in the movies, where people \emph{could} trust your heart.  Where you were holding the gun and you had to choose between shooting the evil clone and shooting your friend, and you just \emph{knew}.



He gestured around us with one hand. ``\emph{This} doesn't work.  This is going to lose us the fight, and all the danger we've been through in our fight against the Nine will be for nothing if they win here.''



I shook my head.  ``I don't disagree, but that line of thinking isn't going to make me drop the gun.''



``Then can I try acting from \emph{my} heart?''  he asked.



Before I could respond, he started approaching me.  I backed away a step, kept the gun leveled, but I couldn't bring myself to shoot as he advanced.



He stepped in close, ignoring the gun, and wrapped his arms around me.  My forehead pressed against his shoulder.  It wasn't the most comfortable hug I'd had, not that I'd had many.  It felt awkward, stiff, clumsy.  But somehow that made it feel more right, like a real hug would have felt off somehow.



He was warm.



\emph{Grue?}



Then, without waiting for me to give an answer, Grue stepped back, taking hold of my left hand and pulling.  I followed without complaint.  I couldn't complain.  If I doubted him \emph{now}, after this-  I'd be ten times as angry at myself as he was with me.



``Priority number one, we get in contact with Cherish,'' Tattletale said, grinning.  ``From there, we can decide whether we want to track down Panacea or go after the Slaughterhouse Nine.''



``Right,'' I said.



``Keep checking your cell phone.  The second we have service, call Coil.''



``Coil is?''



``Our boss, and since he's hidden away, he won't be affected, so he'll be able to place the name and fill us in on the details the agnosia has blocked from us.''



``Okay.''



``It's not the end of the world after all,'' Tattletale smiled.



I nodded.  I was acutely aware of the gun in my right hand.  I felt like I should put it away, but with the way we were moving and my general sense of unease, I couldn't stop and do it.  Hated this.  It reminded me of school.



The reminder made me angry, and it somehow made all of this seem \emph{worse}.  I muttered, ``Sooner we're fucking cured of this miasma, the better.''



``Hey!''  Tattletale paused, pointing at me with a stern expression on her face.  ``Don't swear!''





