





``Your powers are working alright?'' Tattletale asked.



I nodded.



``Bug powers, was it?  Don't want to get it wrong.  Control them, see through their eyes--''



``No.  I can't see through their eyes or hear what they do.  It's mainly touch.''



``Just wanted to check.''  She paused.  ``If I asked you what my power was?''



I shook my head.



``Okay.  And if I said I was born in Mexico, could you tell me where I was born?''



``Didn't you just say?''



``Yeah.  Repeat it back to me?''



``You were born in Mexico?''



``Your short-term recollection is still good, at least.  That would be why you can retain the information Grue and I have shared over the past few minutes.  That big beetle of yours, you named it?''



I glanced at Atlas, who was crawling a short distance away.  ``Atlas.''



Tattletale nodded.  ``That would be the short-term memory, again. Your power probably gives you enough contact with it that you don't lose track of who and what it is.''



``Right.''



``So long as that keeps working, we don't need to worry about you and Grue forgetting who we are in the middle of a conversation.  But for \emph{us}, we might lose track of each other if we split up, so let's stay close, okay?''



``Okay.''



She reached out and took my hand.



``Can you use the bugs to scout our surroundings?  This will go more smoothly if we don't need to worry about running into people.''



It made sense.  I sent my bugs out to cover the surrounding area.



The red mist was everywhere.  Color was strained out, leaving everything a monochrome red.  I could still make out the surroundings, but just enough light was filtered out that the area had settled into an oppressive gloom, with many existing shadows made nearly opaque as a result.  The drifting movements of the mist and the subtle shifts in color and shadow made me feel like things were prowling in every corner and in the edges of my field of vision.



That deep, primal prey-animal part of my psyche kept telling me something was wrong, that I was in danger.  I tried to tell myself that it was just my fear working itself up, my brain playing tricks on me.  There was nothing out there.



The weight of the gun in my hand was both a reassurance and a burden.  It would be so easy to do something I would regret for the rest of my life.



``Hate this,'' I muttered.



``Me too,'' Grue answered.  He put his hand on my shoulder to offer some reassurance.  ``But we manage, we cope because we're a team.  We \emph{belong} together.''



My awareness snagged on someone who was walking a distance behind us, measuring their pace with ours.



``We may need to stand together as a team sooner than later,'' I said. ``We're being followed.''



``By who?'' Tattletale asked.  She paused, then laughed.  ``Silly question, I guess.''



``Tie them up?''  she suggested.



``Right.''



My bugs gathered in out of the way spots, and the spiders began drawing out lines of silk in preparation.  I didn't want to inform this person that I was on to their tail.



Then, just in case they decided to drop the tail and attack us, I began to gather bugs together into decoys.  Human-shaped lumps and clusters of bugs gathered in alleys and at the edges of rooftops.  Still more gathered in the street, standing in alcoves and in other hiding spots.  I invested less bugs in the ones that were further away from our pursuer, trusting that the shadows the miasma cast would help round them out.  There were no decoys our pursuer would see from where they stood, but there were now enough to give them pause.



Grue drifted away from our group to approach one of the decoys.  He extended one hand and traced his fingers through the massed bugs.  ``You're versatile.''



I felt a little uncomfortable at the compliment.  ``We should keep moving.''



``You're not tying them up?''



I shook my head.  A miscommunication on that front.  Hadn't I recently been thinking about chemistry and intuitively understanding how your teammates operated?  The miasma might be throwing us off in that department.  ``Sorry.  Need to prep for it first, I'll make my move in a minute.  For now, we should act normal.''



``Fine.''  He dropped his hand to his side and rejoined us.  We kept walking.  I had to admire them, the way they were confident enough to avoid looking over their shoulders.  I had my bugs to track our pursuer with, and I was \emph{still} feeling nervous having them behind me.



``Is paranoia a side effect of this mist?''



Tattletale nodded.  ``Could be.  As the symptoms progress, you could have fits of anger, paranoia, hallucinations\ldots''



I swallowed.



``Or it could progress in another direction.  A broader agnosia, with the inability to recognize \emph{anything}, not just people.''



``Let's hope it doesn't come to that.''



She nodded.



``I'm going to bind her now.  If it doesn't work, or if she has a way of breaking free, we should run, with the decoys for cover.''



Tattletale just smiled.



The bugs swarmed our pursuer.  I'd minimized the number of bugs on them, just to be safe, with the drawback that I wasn't getting a full picture of who they were.  The bugs couldn't get to her flesh to sting or bite her, but they were telling me she was female in general shape.



I had them deploy the silk they had prepared.  I focused my efforts on her arms and legs.  It took only a couple of seconds to get the threads in place.



She tripped as the silk went taut mid-stride.  Raising one hand to try to catch herself, she found silk threads hampering those movements as well.  To avoid landing face first, she twisted herself in mid-air so she hit the ground with her shoulder instead.



``Got her,'' I said.  ``Let's keep going.  We can lose her.''



``We should investigate,'' Grue said.  ``Make sure she isn't a threat, and deal with her if she is.''



``With this miasma affecting us, there's no way to be sure of exactly of just who we're \emph{dealing} with,'' I pointed out.



``We have Tattletale.  She can tell us if this person's a member of the Slaughterhouse Nine.''



``Tattletale's not--''



I stopped.  Where had that come from?



``What?''  Grue tilted his head as he looked over his shoulder at me.



``I was going to say she's not always right, but I've still got that black hole in my memory of her, so I'm not sure where that's coming from.''



Grue rubbed his chin.  ``Something to keep in mind, but I still think we should check this person out.''



``I agree,'' Tattletale said, a slight smile on her face.  She tugged on my hand.  ``Come on!''



We had to stick together.  I reluctantly followed, knowing that separating from the group could mean losing them altogether.



We stopped a few hundred feet away from the woman.  The silk strands had formed a cord around her arms and legs, and the work of the spiders had tightened the binding as she allowed it to slack.  She hadn't made it back to her feet after falling to the ground.



Grue drew a knife.



``Hey,'' I said.  I grabbed his arm.  ``What are you doing?''



``She's \emph{obviously} a member of the Slaughterhouse Nine,'' Tattletale said.



``Fill me in?  Because I must have missed something.  Doesn't seem that clear to me.''



``Think about it.  Why is she wearing a mask like that, if not to filter out the miasma?  She knew about it in advance.''



``Maybe,'' I said.  I\emph{ could }make out something like a gas mask or filter, now that Tattletale had pointed it out.\emph{  }``Maybe there's another explanation.  It could have something to do with her power?''



``It doesn't,'' Tattletale said.



Thinking about killing someone was one thing.  I'd always assumed I might have to do it out of necessity to save a teammate\ldots I'd even come close to doing it when attacking the Nine, not long ago.  Couldn't recall who it had been, but I'd gone all out, used potentially lethal stings and bites.



That had been at a distance.  Now we were looking at killing someone face to face.



The mask, there was another reason for it.  The-



Tattletale interrupted my thoughts.  ``If you guys aren't going to do it, I can.  She was following us, she was prepared for the miasma, and I'm positive she's a bad guy.  My power, you know.''



``We can't be certain,'' I said.



``With my power, I'm five hundred percent sure.  Trust me,'' she said, grinning.  She started toward the heroine.



``No,'' I said.



``Skitter's right,'' Grue said.  ``She could be playing possum.  Best to avoid being reckless.  Keep our distance and finish her.''



``That's not what I meant.  Let's just leave,'' I said.  ``I'll make that phone call to, um--''



``Coil,'' Tattletale supplied.



I nodded.  ``We'll get the information we need, get ourselves cured, or track down the Nine.''



``Cherish could lie,'' Grue said.



It took me a second to place Cherish's name.  Names were slipping from my mind too easily.  ``Maybe.  We'll use our own judgement to corroborate her facts.''



Tattletale scowled, ``Have you forgotten how aggressively we've been going after the Slaughterhouse Nine?  The attacks, the harassment, capturing Cherish and Shatterbird.  And now you want to leave one of them there?  We don't have to get close to her to take her out.  You have the gun.''



I stared down at the weapon in my hand.



``Trust me,'' she said.



``No.''



Both Tattletale and Grue turned to look at me.



``No?''  Grue asked.  ``We're a team, Skitter.  We're supposed to trust one another when the chips are down, have each other's backs.''



I didn't like the implications of that.  Like I was failing them.



But I shook my head.  ``No.''



``Explain?'' he asked.  He looked calm, but I could see the irritation in his posture.  Was the mist getting to him?



``The miasma\ldots if it makes us paranoid, it could be coloring our perceptions here.  Even Tattletale's.''



``I would know if it was,'' she said.  She seemed impatient.



``Maybe.  But I'm not certain enough about that to take another life.''



``You nearly took Siberian's,'' she retorted.



``Yeah.  Sure.  But that was different.''



``I don't see how.''



I stared at the bound woman who was prone on the ground, half-covered in my bugs.  She was looking in my direction.



``It bugs me.  This is too easy.  If the Nine were this easy to take out, we wouldn't be in this situation.''



``Sounds like a pretty thin justification for backing out,'' Grue said.



``Yeah,'' Tattletale added.



This kind of social pressure wasn't the sort of thing I was good at coping with.  Just going by my recollection of how we'd planned many of our capers, I could usually trust some of the others to have my back when I was arguing a point.  Or I'd had some other motive or reason to go along with them.



``Why are you pushing so hard for this?''  I asked.



``Did you forget what they did to me?''  Grue asked, his voice cold.



\emph{Him specifically?  }I had forgotten, yes.\emph{  }But I could remember that scene, the emotions then, every feeling that I'd experienced afterward.  Frustration, hate, pain, sympathy for the pain he must have experienced himself.  I could remember the feeling of heartbreak, because someone I cared about was gone, in a sense.



``No,'' I replied.



``Where's your anger, your \emph{outrage}?  Or don't you care?''



``I care!  It's--''



``Then \emph{end} this.''



I shook my head, as if I could clear it.  It wasn't that I wasn't thinking clearly, necessarily.  It was that my thoughts kept hitting that dead-end where I couldn't reach back for context about people, about Tattletale and Grue and the Nine.  I was in the dark.



What I did know was that I'd done too many things I regretted.  I wasn't about to add something as serious as murder to the list.



Grue must have seen something in my posture, because he shook his head and turned away.  ``Give me the gun, then.''



``Just use your power,'' Tattletale told him.



``I want Skitter to acknowledge that she doesn't care enough about this team or about \emph{me} to do what's necessary.  She can do that by admitting she doesn't have the courage to shoot and allow me to do it.''



``That's not what this is about,'' I said.  ``Murder is \emph{serious}.  You don't kill without being \emph{absolutely} certain it's right.  And nothing's certain for as long as we're under the influence of this miasma.''



He scoffed.  ``And you call yourself a supervillain?''



``I call myself Skitter.  If someone wants to stick me with some other label, that's their issue to deal with, not mine.''



``You're not giving me the gun?''



``No.''



He shrugged, ``So you don't care at all, about what happened to me.  You don't care about this team.  And you'll even look down on us while you do it.  Your \emph{contemptible }friends.''



``I care.  More than you know.  But you told me, not long ago, that I should follow my heart, trust my gut.  Fine.  That's what I'm doing.  You attack her, I'll fight to save her.''



He barked out a laugh, ``You'll fight \emph{me}?  You're a traitor now?''



The word hit home.  I must have flinched.



``A traitor \emph{again},'' he added.



I snapped my head up to look at him in surprise.



``I wonder what it says that the notion of you being a traitor is so ingrained in my impression of you that it jumps to mind, even with the mist affecting me?''



``That's enough,'' I said.



``I know you like me.  I can read it on your face, I could see the way your eyes widened when you heard my name.  You're an open book in some ways.  And I'll tell you right now, I'm pretty sure I'm in love with you.''



I felt a nervous feeling deep in my gut.  It wasn't pleasant, at stark odds to what he was saying.



Grue's words spoke to that feeling of trepidation.  ``But this?  It's telling me I could never have a relationship with you, never be close to you, because I'll always wonder if you'll stab me in the back or fuck me over, fail to do what's necessary in a situation like this.  I'll never be able to shake that image of you as a traitor.''



He kept saying that word, \emph{traitor}, hammering it in.



``Unless I take this gun and shoot that woman, who you're convinced is a member of the Nine,'' I guessed what he was getting at.



``Guess I had the wrong impression of you,'' he said.  The emotion in his tone was so different that it caught me off guard.  Almost contemplative.  If I thought of it as him emotionally closing down, it almost fit with the impression I associated with Grue.  At the same time, it didn't quite jibe with what I was seeing.  Again, I felt that distinct discomfort.



\emph{Is this how I lose my mind?}



I shrugged.  ``I guess you did.''



I carefully holstered the gun, as if hiding it could keep it from coming up again in conversation.



A long pause reigned.



``I'm disappointed, but there's nothing I can do about that,'' he said.  Then he smiled.  He turned and began walking away.  ``Let's go.''



``Just like that?''  I asked.



``We're leaving her?''  Tattletale asked.



``Seems we have to.  Tattletale, can you use your power to make sure the lady from the Nine doesn't pose a danger?''



Tattletale nodded, smiling.



``Then let's hurry.  We wasted too much time here.''



``Let me know when she's not in your range anymore,'' Tattletale said to me.  ``I'll try to use my power to make sure she isn't following us.''



I nodded.



She hugged my arm, ``You're stubborn, but we're still friends, right?''



I nodded again.  I felt like I was back in school, in a situation where I couldn't say anything without saying the wrong thing.  Strange, to recall being around the bullies rather than in the company of my team.



The argument weighed on me, as did the things Grue had said, the judgements.  Had I been wrong?  Were we risking letting one of the Nine get away, to murder others?  Was I arguing because I was still clinging to old ideals, or because the miasma was making me divisive?



Even if the miasma was to blame, I hated the idea of failing the others yet again.



This situation was fucking with my head.  I still felt like I was in the middle of a fight, that heart pounding mode where I was ready for bullets or laser blasts to start flying, for me or a friend to be in mortal danger, where a split second response meant the difference between life or death.



Except there was no danger here.  The only people nearby were the woman we were leaving behind, Grue and Tattletale.



I glanced at Tattletale as we ran.  Could I trust them?  They had been in the miasma for a little longer than I had, and I was already experiencing what I could only label as paranoia.  With only a difference of minutes, Legend had been thrust into a paranoid state where he was taking a reckless, offensive course of action, eliminating \emph{everyone} from the battlefield, regardless of whether they might be friend or enemy.  How much was it affecting these two?  How would it influence their actions?



More to the point, what was my best course of action here?  If I worked on the assumption that I could trust them, would they drag me into a situation that was just as bad as what we'd gone through with the bound woman?  Or if I \emph{didn't} trust them, if I allowed myself to become suspicious and take countermeasures, would that be a slippery slope that led to me trying to kill them, in fear for my own life?



We'd come close to fighting just now.



``You're awfully quiet,'' Tattletale said.



``Leave her be,'' Grue told her, his voice low.



What was I supposed to do?  I didn't trust myself to handle this alone, not with the speed at which this general unease was building up.  But I wasn't sure I trusted them either.  Something about the argument, it felt off.  Wrong.



``She's out of my range,'' I said.  ``Tattletale?''



``I'll keep an eye out!''  She grinned.



\emph{Traitor}.  I could almost hear the accusation.



I'd lied.  The woman was still in my range.



``Is there service?''  Grue asked.  I must have looked confused, because he clarified by saying, ``The phone.''



I pulled my phone out of the space between my breasts and the armor at my front and checked the display.



``Yeah,'' I said.  \emph{Why does that bug me?}



``Call Coil,'' Tattletale reminded me.  ``We need to know where Cherish is.''



I found him in the contact list and made the call.



``Speaker phone?'' Grue suggested.



I nodded, selected the option and hit the button.



As the first ring sounded out, my swarm sense alerted me to the bound woman breaking free of the silk strands, as if it was effortless.  Had she been playing possum after all, hoping we would get close?



I looked at Tattletale, trying to see if had any inkling that this supposed member of the Nine was free.



Nothing.  Tattletale turned to me and grinned.



``No trouble incoming?''  I asked, as the phone rang again.



She shook her head.  ``All good.''



Was her power not working as well as she'd thought?  I couldn't even recollect what it was, but she'd said she would keep an eye out\ldots and there was something alarming occurring this very moment.



``Skitter,'' Coil answered the phone.  ``I've been made aware that Bonesaw has deployed the ace she had up her sleeve.''



``Yeah.  Agnostia\ldots Agnosia-inducing mist.  Permanent, according to Tattletale.''



``I see.''  I could hear the sounds of typing on a keyboard.  ``Agnosia\ldots Panacea can't reverse the effects?''



``She's not here.  We're trying to find her.''



``And you need Cherish for that, I suppose.''



I was grateful that he was supplying the names, because it meant I didn't have to bog down the conversation by remembering or asking.  Grue, Tattletale and I had brought them up recently enough that it wasn't a huge leap to remember their names.



The woman who I'd tied up with the spider silk was walking towards us.  Her progress was hampered by the decoys.  I kept my mouth shut.  It wasn't an \emph{imminent} problem, and I was more interested in gauging just how far gone Tattletale's power was.



``Except that with the agnosia, we can't remember where she is and go meet her.''



``Meeting Cherish would be a grave error,'' Coil spoke.



``Just put us in contact with her, then?''



``Tattletale informed me of your code.  You remember how it's put together?''



``Yeah.  My memory's fine, it's just my ability to identify people and remember stuff about them that's fucked up.''



Tattletale glared at me.  Right.  She didn't like swearing.



``Then, using a name we're both familiar with, D-gangrene.''



``I can't remember names.  I don't think I can use the code.''



``Troubling.  You must understand my predicament.  For all I know, you're a third party using Skitter's voice to make the request.  With shapeshifters, empaths and other methods of coercion, I have to be very careful about the dissemination of information.''



``I know.''



The woman was still approaching.  Tattletale and Grue weren't talking.



Something was wrong.



``What if we kept you on the line?''  I suggested.



``That will suffice.''



There was a pause, then the sound of background noise.  A ring sounded, different from the one before.  It was interrupted as Cherish picked up.



``I have never been so sorry to miss out,'' Cherish said.  She sounded a bit hoarse.



``We're requesting your help,'' Coil spoke.



``Oh, you need my help in more ways than you're aware of.  Not that I'm going to provide it.  Skitter's on the line, I believe?''



``She is.''



``I'm here,'' I confirmed.



``And Tattletale and Grue, of course.''  She chuckled.  ``How amusing.  Seems like I'm in high demand.''



``They're looking for Panacea,'' Coil said.  ``Identifying her for us would be one way to achieve revenge on the Slaughterhouse Nine for turning on you.''



``Revenge?  Not my interest in the slightest.  I've learned my lesson and I've become the poster child for team loyalty.''



Coil paused, then said, ``I'm prepared to offer you some enticements.  I imagine your current quarters can't be too comfortable.''



``Don't suppose these enticements will be hand delivered?''



``They will be provided by remote control, as your food has been.''



``Some headphones and music would be nice,'' she said.  ``The sound of the waves banging on the hull is driving me crazy.''



``Such could be arranged.''



``Nah, I'm totally fucking with you.  Music, as if.''



There were too many things that seemed off.  Cherish's tone among them.  I glanced around.  The woman was still following us, throwing herself after decoys, verifying they were false, then retracing her steps.  She was slowly closing in.  I positioned Atlas so he would be ready to distract her if it came down to it.



``You're stalling?''  Coil asked.  ``I don't see the point.''



``Just trying to see if I can provoke a reaction from you.  There's only so many times I can read the labels of the shipping containers before I lose my mind.  Have to amuse myself somehow.''



``What will it take for you to tell us where Panacea is?''  Coil asked.



``Oh, I'm feeling generous, and I want to see what happens.  I'll tell you that as a freebie.  They're at Arcadia.  Somewhere in the top floor.''



\emph{A freebie}.  Something was going on, and I wasn't aware what.  I had to piece it together, but I had so little information.



``And maybe \emph{I }could offer \emph{you} something, in exchange for some goodwill.  Maybe you'll even want to let me go free, no obligations.''



The feeling of dread that had been following me wasn't getting worse as the woman approached.  It was staying steady, like someone had a gun pointed at me, and they'd had it aimed my way for some time now.



``I'm listening,'' Coil said, ``But if this is frivolous or another waste of our time--''



``Nah.  Critically important.  I'll trust that you'll take it for what it's worth and repay me in kind.''



``What is it?'' I asked.



``Oh, it's simple.  Going by what I've been able to observe around the city, there seems to be a major concern.  \emph{Si Jack effugit civitatem, mundus terminabitur}.''



``I'm not versed in Latin,''  Coil spoke, sounding annoyed.



``For shame, Coil, for shame,'' Cherish said.  Her voice was too cheerful. ``You can't sell the cultured supervillain image without the ability to make quips in an ancient language.  I had the benefit of my power, languages are easier to learn when you can get a sense of what the other person's feeling.''



``That was something about Jack?''  I asked,  ``Repeat that in English?''



``Doesn't matter anymore,'' she replied.  ``The message was delivered.  I'll leave you to think about it.''



If only I could have blamed the miasma for my idiocy.  Everything clicked into place.



I kept my voice level, ``I don't think you'll get much goodwill if we don't understand what the fuck you're talking about.  Coil?  We're moving out now.''



``Report back when you've found the healer,'' Coil told me.



I hung up before Cherish could speak, then I glanced at the others.  ``Let's go?  Arcadia high?''



They nodded.



My heart pounded with such force that my vision wavered.  I turned to head toward Arcadia high, joined by the two members of the Nine.  \emph{Stay calm, don't let on that you know}.



If I could direct the woman to us\ldots



The miasma's effects had almost made me lose track of her.  She was fighting, grappling with mechanical spiders.  She went from fighting like an ordinary individual to moving at high speeds and throwing crushing punches, then back again.  I couldn't think of how to help her, and she was obviously unable to help \emph{me.}



Cherish had been engaging in double-speak, saying one thing to us, while addressing the two people with me the entire time.  She'd told them about where she was being held captive, and she'd offered the most valuable information she had to avoid getting tortured to death after they'd freed her.  From the way she'd talked about the message being received, one of the people with me had to be Jack.



Jack was slated to bring about the end of the world if he left Brockton Bay, and now he \emph{knew}.



Couldn't meet their eyes, didn't want to speak, in case I let on that I knew.  I could barely breathe, I was so afraid of letting my emotions show.



My gun was in the compartment at my back.  I'd put it away at the conclusion of our argument, and with the compartment broken in my fall from Atlas's back, I'd been forced to put it in a place where it wasn't easy to draw.  I couldn't be sure I would be able to draw it and fire.  I was still handicapped, unaware of their powers.  I was fighting blind.



If Jack or the girl killed Amy, just about everyone in the city would die violently from the miasma's effects.  But I couldn't stop them without letting on that I knew.  Fighting them put me at a clear disadvantage, and-



``Skitter,'' Jack spoke.



I didn't waste time turning to face him.  I gripped the hair of the blonde girl beside me and virtually hauled her off her feet as I dragged her around to a position between Jack and myself.  Jack was already swinging his knife.



The knife cut the girl more than it cut me.  I could feel it raking across the exterior of my costume, failing to penetrate, but he was swinging it underhand, and it caught me in the chin, slicing through the side of my cheek and up to my temple.



I tried to keep a hold on the girl for the sake of using her as a human shield, but I saw her reach into her dress and withdraw some vials.  I shoved her toward Jack, then stepped forward to kick her square between the shoulder blades.  She collided with him, interrupting his follow-up swing.  For good measure, I drew the bugs from beneath my costume and sent them chasing after her.  Some capsaicin-laced bugs, just the few I had remaining.



Jack caught her shoulders and spun her around so she faced me.  The vials were already billowing with a chemical reaction.  She threw them at me.



I backed away, and they hit the ground between our two groups, black smoke joining the crimson mist around us.



``You've outlived your usefulness, Skitter,'' Jack spoke.



\emph{If I'd just had a minute or two more to decide on a course of action}.



``It was fun.  I almost wish I'd nominated you for the Nine.  You're versatile, and there's so many weak points I could have exploited if I'd had more time.  If Cherish's information on you wasn't so misleading, I think I could have made you shoot the heroine.  To corrupt you like that, it would have been amusing.''



I fumbled for the gun, using my bugs to get a sense for where it was.  In the same motion that I pointed it, Jack slapped it out of my hand with two slashes of his knife.  He was a dozen feet away, but the knife nonetheless connected with my weapon.



My bugs began to gather like a dark cloud, their mass casting a shadow on the already gloomy surroundings.



``So I end the world?  Interesting.''



``The source is a little unreliable,'' I lied.



``Still, I would love to see how that comes about.''



``You won't live to,'' I told him.



``I'll make sure he does,'' the girl informed me.



My swarm could feel others approach from the heroine's direction.  They were the size of dogs, and they skipped forward on mechanical legs.  The mechanical spiders.  Dozens of them, coming straight for me.



If I was judging right, they were running faster than I could.



I sent the swarm after Jack and the girl, massed into thousands of bugs.  Some groups clustered so tight together that they looked like massive, amorphous black entities, amoebas floating through a cityscape painted in shades of red and black.  Atlas heard my call and headed my way from the place I'd positioned him, too far away to join the fight for a minute or two.



The girl was already mixing something else together.  Plumes of white smoke billowed around her, almost luminescent after so long spent in the crimson mist.  My bugs died on contact with the gas.



Everything I'd learned about my enemies had been blocked.  I had no information on them, no sense of what to expect.  They weren't so handicapped.



She tipped half the vial's contents into an empty container and handed it to Jack.  Both protected from my power, they started backing away.



I moved to edge around the cloud of black smoke, but Jack struck me with the knife.  I had to use my forearms to cover my unprotected face.  I just had my glasses, some bugs, and a layer of cloth protecting it.  Nothing that would guard against Jack's cuts.



When I'd lowered my arms, they had already turned a corner, running in the general direction of Arcadia high.  Running around the cloud of black smoke cost me a precious minute.  I made my way around the same corner they'd rounded, and stopped short as I came face to face with another black cloud.



Couldn't match their speed, not with these noxious clouds slowing me down.  With the heroine lying unconscious in the street, several blocks in the wrong direction, I had no allies to turn to.  Worse, anyone I came across was as likely as not to be a threat. It was down to Atlas and me, and Atlas was especially vulnerable to both of my opponents.  I couldn't even fly after them without risking being cut down in midair.



I had minimal information on my opponents, while they knew enough about me to completely counter my powers.  Topping it all off, the mechanical spiders were steadily, inexorably closing in on me.  I'd lost my last fight with the things, and there were dozens more this time around.  Couldn't fly without exposing myself to Jack's power, couldn't stay on the ground without getting swarmed.



I swallowed hard and held out one hand to grab Atlas's horn as he landed.  In a moment, we were in the air, giving chase.



I wasn't thinking about winning anymore.  I was thinking in terms of minimizing the damage when we lost.





