





Arcadia high was the school every kid in Brockton Bay wanted to attend.  A big part of that was the fact that \emph{everyone} knew that the Wards attended Arcadia, and attending meant that any one of your classmates could be a superhero or superheroine.  To anyone else, \emph{you} could just as easily be one, too.  It wasn't a rich kid's school like Immaculata, but it was a \emph{good} school.  Every classmate treated other classmates with the utmost respect.  Both the students and the school itself maintained a certain status and pride as a consequence.



Now it was something else, and it inspired entirely different feelings.  The front gate looked like it had aged a thousand years, the sharp corners of the cut stone had rounded off, the ivy that once wound around it had withered.  The windows of the building were all shattered, empty of glass, and the fields were a patchwork of overgrown grass and mud.  With the faint tendrils of colored mist that surrounded the grounds, it looked like a prime location for a horror movie.



I had little doubt I was in the right place.



\emph{Panacea's the healer}, \emph{top floor}.  \emph{Jack is the slasher, the blond girl the chemist-tinker}.  \emph{Panacea's the healer on the top floor, Jack is the slasher, the blond girl is the chemist.}



I recited the words as a refrain, as if I could hold the names and identities of the major players in my short-term memory by constantly reminding myself of who they were.



The school was on a hill, meaning the water that was producing the miasma was far enough away that only traces of it reached this far.  The little vapor that got to the school was held at bay by the stone wall that ringed the school.  The design suggested it had been intended more for aesthetics than for utility, but it was serving a purpose nonetheless.



\emph{Panacea's the healer}, top floor, \emph{Jack is the slasher, the blond girl the chemist-tinker}.  \emph{Panacea is the healer, top floor, Jack is the slasher, the blond girl is the chemist-tinker.}



It seemed like the mechanical spiders had lost track of me.  They would probably give up the chase and return to their master, but it was one less thing to worry about for the time being.



Jack and the tinker would have gone in through the ground floor.  I decided to land on the roof.  The second I was on terra firma, I reached for my phone to check.  No signal.



I needed to signal someone about what was going on.  I was woefully underequipped, and I doubted my ability to win this alone, especially when my opponents weren't as disadvantaged as I was.



I \emph{could} use something like a giant nine crafted out of bugs floating over the school to signal that the pair was here\ldots but there was no guarantee that someone would come.  There was also the possibility that it would lead to the good guys dropping another bomb on us.  That would get the healer and maybe even me killed.  Panacea \emph{had} to survive, or everyone in the city would die in the aftermath of Bonesaw's miasma.



\emph{Panacea is the healer, she's on the top floor, Jack is the slasher, the blond girl is the chemist-tinker.}



I tenderly touched the cut on my face.  Jack must have pulled back as I used the tinker as a shield, because the cut was fairly shallow.  It was long, though, and my fingertips were wet with blood after I touched my hand to it.  I couldn't distinguish the blood from the black fabric of my gloves, so I couldn't tell how much it actually was.  I wasn't sure I wanted to know.



There was a door on the rooftop, and I used my knife to pry the doorknob partially off, then gave it a firm kick to remove it.  The lock was built into the handle, and it didn't take long to figure out how to open it when I could see the internal mechanisms.  It wasn't exactly high security, more intended to keep kids from getting onto the roof than keeping people on the roof from getting in.



Just past the door was a set of stairs that led down into the top floor of the building.  It looked like a janitorial closet.  I sent Atlas down to check before venturing down myself, and I began distributing my swarm through the school.  I prepared silk lines across doorways and hallways to inform me of others passing through, placed ants, earwigs, centipedes and pill bugs on the walls to give me a sense of the layout, and sent flies to scan the interiors of each room to see if I couldn't find anyone.



Again, I repeated the refrain in my head, reminding myself about who was in the building.  I wasn't sure it was helping, but I didn't want to get tricked again.



There were two hallways and three classrooms my bugs couldn't enter without dying on the spot. That marked out a relatively small area that the Nine could be.



The biggest issue was that I couldn't find Panacea.  Did that mean she was in close confines with the enemy?  It wasn't a good thought.



As I laid silk lines across possible entryways to alert myself about enemy movements, I was careful to check each area before I advanced further into the building.  My eyes searched for details while my swarm scanned the walls and the ground.



I was a short distance away from the Nine when I saw a wet spot on the wall, complete with discoloration of the paint.  I sent bugs in, and they felt shards of glass on the floor around the patch.  I wouldn't have said that the swarm \emph{smelled} anything, but there was something heavy in the air as flies beat their wings, the muscular action simultaneously drawing oxygen in.  Whatever it was, it was dense, cloying, odorless and colorless, only extending a dozen feet around the spot.



I backtracked and picked a different route.  My pace slowed to half of what it had been as I searched for other telltale details.  Twice, I found similar traps, both with that odourless smoke, and twice I had to change my route.



I paused outside the bug-killing zone.  Flies had ferried spiders to me, and I started organizing them to produce lengths of silk cord.  I left them behind while I creeped closer and listened in.



``\ldotsminds do think alike.  I did something very similar for Siberian.''  A girl's voice.



``Shut up.  We're \emph{nothing} alike.''  Another girl.



``We could be!  Haven't you ever wanted to start over?  I could make you younger!  We'd be the same age!  And wear matching outfits!  Oh!  I could do plastic surgery, we could be twins!''



``Did- did you do that to yourself?  Make yourself young?''



``No.''  A male voice.  ``Rest assured, Bonesaw's immaturity is genuine.  Both an asset in how it makes her that much more creative, free in her ways.  A detriment in other ways.''



``Doesn't\ldots that bother you?  Him saying that about you?''



``Jack knows what he's doing.''



``I do.  I know a lot of things,'' Jack spoke, his voice smooth, almost seductive.



``Don't.  I know you've got a silver tongue.  I don't want to hear it.''



``You prefer the alternative?''  Jack asked, his voice cool.



I could picture him holding that knife of his, the threat all too clear.



There was a long pause.



He spoke, ``I suppose not.  So let's dialogue.''



``Go ahead,'' Panacea's voice was small, almost defeated.



``What's holding you back?  You're capable of so much, of changing the world, of destroying it, but you're so very small, Amelia Claire Lavere.''



His voice was almost mocking as he said her name.



``That's not my name.''



``It's the name you were born with.  Imagine my surprise when I found out your relation to Marquis.  In my last visit to Brockton Bay, I crossed paths with each of the major players.  I met the man.  I must tell you, Amelia, he was a very interesting character.''



``I don't really want to know.''



``I'm going to tell you.  And I have another motive, but I'll get to that in a moment.  Marquis was a man of \emph{honor}.  He decided on the rules he would play by and he stuck to them.  He put his life and limb at risk to try to keep me from killing women and children, and I decided to see if I could use that to break him.  I admit I failed.''



``He killed Allfather's daughter.''



``No, Amelia, he didn't.''



There was a pause.



``Did \emph{you }kill her?''



``No.  What I'm saying is that Marquis would not have killed the girl, even under duress; that was one of the rules he set for himself.  If he was going to violate that rule, he would have done it when I'd tried to break him.''



``Allfather put a contract on my head before he died, because of what Marquis did.  Because- It's how I found out he was my dad.  A letter from Dragon to Carol.''



``Carol\ldots Ah yes, Brandish.   Well, I suspect either Dragon was manipulating you, or your father was manipulating \emph{Dragon }in an effort to get a message to you.''



``A message.''



``That he's there, that he exists.  Perhaps he sought to ensure he wasn't forgotten by his child.  He was an old-fashioned individual, so it makes sense that he'd seek immortality through his progeny.''



Bonesaw piped up.  ``That's stupid.  Why do something like that when someone like me could make you immortal for real?''



``Shush, now.  Finish sewing yourself up while Amelia and I talk.''



``Okay,'' Bonesaw said.  Her voice overlapped with Panacea saying, ``Stop saying that.  It's not my name.''



``Isn't it?''



There was another silence.



``You're your father's daughter.  Both of you are bound up in rules you've imposed on yourselves.  His rules defined his demeanor, the boundaries he worked within, the goals he sought to achieve and how he achieved them.  They were his armor as much as his power was.  I would guess your rules are your weakness.  Rather than focus you, they leave you in free fall, nothing to grasp on to except your sister there, and we both know how \emph{that} has turned out.''



\emph{Sister}.  I made a mental note of that.  There were four people in that room.



``I- how do you know this?''



``Our emotion reader picked up on some.  I've figured out the rest.  As you might expect, I'm rather familiar with damaged individuals.''



Bonesaw giggled.



I didn't like the way this was going.  I looked down the hall to see the doors.  Each door had once had a window on the upper half, but there were only slivers left, the rest scattered over the floor.  In an ideal world, some distraction would present itself, or the conversation would become a heated argument and they would distract each other.  I could rise from my crouching position, step forward, aim my gun and fire.  Unload the gun's clip on Jack and Bonesaw.



Or I'd miss, resulting in the messy deaths of Panacea, her sister and I.  I really needed that distraction if I was going to do this.



``I'm not\ldots not that type of damaged.  I'm not a monster,'' Panacea protested.  As an afterthought, she added, ``No offense.''



``I've been called worse.  I almost relish being called a monster.  As though I've transcended humanity and become something from myth.''



``Myth.''



``And according to Cherish, it may well be a destruction myth.''



``What?''



``She recently informed me that the world is going to end because of me.  Not quite sure how or when.  It could well be that I'm the butterfly that flaps his wings and stirs a hurricane into being through a chain of cause and effect.''



``I don't want the world to end,'' Bonesaw said.  ``It's fun.''



``It is.  But I expect it won't end altogether.  There's always going to be survivors.''



``True.''



``And it makes for an interesting picture.  After everything's gone, there'll be a new beginning.  Who better to craft the remains into a new world than you and Mannequin?''



``And Amelia?''



``And Amelia, if she so chooses.  We could be like gods in a new world.''



``You're crazy,'' Panacea muttered.



``According to studies, clinically depressed individuals have a more accurate grasp of reality than the average person.  We tell ourselves lies and layer falsehoods and self-assurances over one another in order to cope with a world colored by pain and suffering.  We put blinders on.  If we lose that illusion, we crumble into depression or we crack and go mad.  So perhaps I'm crazy, but only because I see things too clearly?''



``No,'' Panacea's voice was quiet.  ``Um.  You're not going to kill me if I argue, are you?''



``I'm liable to kill you if you don't.''



``It's not that you see too clearly.  I think your view is warped.''



``Over the course of millions of generations that led to your birth, how many of your ancestors were successful because they were cruel to others, because they lied, cheated, stole from their kin, betrayed their brothers and sisters, warred with their neighbors, \emph{killed}?  We know about Marquis, so that's \emph{one}.''



\emph{How many were successful because they cooperated}?  I wondered.



Jack probably had a rebuttal to my question, but I wasn't about to speak up to hear it, and Panacea didn't ask.  She fell silent.



I was tensed, ready to move and shoot the second an opportunity arose.  Anything would suffice.  Anything would do.



I visualized it, the steps I'd take to open fire, and I realized that the shards of glass on the ground between me and the door could provide them with a half-second of warning.  Slowly, carefully, I began brushing the shards aside, keeping my ears peeled for some clue about a key distraction.



``Survival of the fittest, it sounds so tidy, but it's really hundreds of thousands of years of brutish, messy, violent incidents, \emph{billions} of events that you'd want to avert your eyes from if you were to see them in person.  And that's a large part of what's shaped us into what we are.  But we wear masks, we pretend to be good, we extend a helping hand to others for reasons that are ultimately self-serving, and all the while, we're just crude, pleasure-seeking, conniving, selfish apes.  We're all monsters, deep down inside.''



Again, one of those pauses that suggested something was going on that was visual and out of sight, rather than something I could overhear.  Jack offered a dry chuckle.  ``Did that hit home?''



``I'm\ldots not that kind of person.  Not a monster.  I'd kill myself before I became like that.''



``But you see how you could be like us.  It wouldn't even be very hard.  Just\ldots let go of those rules of yours.  You'd get everything you ever wanted.''



``Not family.''



``\emph{Yes}, family.''  Bonesaw cut in.



``You guys kill each other.  That's not family.''



``You're derailing our conversation, Bonesaw,'' Jack chided the girl.  ``Amelia, when I say you could have everything you ever wanted, I'm telling you that you could live free of guilt, of shame, you could have your sister by your side, no more doubts plaguing you, no more feeling down.  Haven't you laid in bed at night, wondering, praying for a world where you could have something like that?  I'm telling you that you can have those things, and I promise you that the transition from being who you are now to being who you \emph{could be} would be much quicker than you suspect.''



``No.''  The defiance was half-hearted.



``Amelia, you could let yourself cut loose and love life for the first time since you were young.''



And just like that, her resistance crumbled.  ``I've never felt like that.  Never felt carefree.  Not since I could remember.  Not even when I was a kid.''



``I see.  From your earliest memory, what was that?  In Marquis's home?  No?  Being taken \emph{home} by the heroes and heroines that would become your false family?  Ah, I saw that change in expression.  That would be your earliest memory, and you found yourself struggling to adjust to your new home, to school and life without your supervillain daddy.  By the time you did figure those things out, you had other worries.  I imagine your family was distant.  So you struggled to please them, to be a good girl, not that it ever mattered.  There was only disappointment.''



``You sound like Tattletale.  That's not a compliment.''



``My ability to read people is learned, not given, I assure you.  Most of the conclusions I've come to have been from the cues you've given me.  Body language, tone, things you've said.  And I know these sorts of things and what to look for because I've met others like you.  \emph{That's} what I'm offering you.  A chance to be with similar people for the first time in your life, a chance to be \emph{yourself},  to have everything you want, and to be with \emph{me}.  I suspect you've never been around someone who actually paid attention to you.''



``Tattletale did.  And Skitter.''



I startled at that.



``I meant on a long-term basis, but let's talk about that.  I imagine they were telling you `No, you aren't.  You can be good.'''



``Yeah.''



``But you didn't believe them, did you, Amelia?  You've spent years telling yourself the opposite.  You're a bad person, you're destined to be bad, by circumstance and blood.  And even though you didn't believe them, you'll believe \emph{me} when I tell you no, you aren't a good person, but that's okay.''



``It's not.''



``You say that, but you believe me when I say it.''



There was another pause where Panacea didn't venture a response.



``Isn't it unfair?  Through no fault of your own, the blood in your veins is the blood of a criminal, and that's affected how your family looks at you.  You've been saddled with feelings that aren't your fault, and doomed to a life without color, enjoyment or pleasure.  Don't you deserve to follow your passions?  A decade and a half of doing what others want you to do, doing what \emph{society} wants you to do, haven't you earned the right to do what you really desire, just this once?''



``That's not really that convincing,'' Panacea spoke, but she didn't sound assertive.



``I know.  So I'll offer you a deal.  If you indulge yourself, we'll surrender.''



``What?''



``I won't even make you do it now.  Just look me in the eye, and honestly tell me you'll do it. Drop all of the rules you've set yourself.  I don't care what you do after, you can wipe your sister's memories, you can kill yourself, you can run away or come with us.  And your side wins.''



``Aren't we winning anyways?''



``Up for debate.  I'm really quite thrilled with the current situation.  Very enjoyable, and we've certainly made an impact.''



``This deal is a trap.  You'll make me do it and then you'll kill me.''



``I \emph{could, }but I won't.  Do you really have anything to lose by trying?  If I'm going to kill you, I'm going to kill you regardless of what you say or do.  Three and a half words: `I'll do it', and we leave the city.''



I almost stood right then, to open fire before she made a decision one way or another.  I had to convince myself to wait, that no matter what they were saying, they wouldn't leave right this instant.



Then I heard the sound of glass crunching in time with someone's footsteps.



With the length of time I'd waited for an opportunity, I was going to take what I could get.  My heart pounded, my hands shook even as I gripped the gun as hard as I could, but I let out a slow breath as I drew myself smoothly to a standing position and stepped into the doorway, pointing the gun through the window frame in the door.



They hadn't heard me move.  It left me a second to take in the scene and make sure I was shooting the right people.



They were in a music room that had been arranged with seats on a series of ascending platforms, backed by windows that had exploded inward, scattering the area with glass shards.  At the bottom `floor', there was a podium waiting for the teacher.  Jack was walking up the steps to approach a girl.  I knew he was Jack because he was the only male present.  He was wreathed in thin white smoke, wore a light gray t-shirt marked with blood stains and black jeans tucked into cowboy boots.  A thick leather belt had a variety of knives, including a butcher's cleaver, a stiletto and a serrated blade.



His teammate Bonesaw, was standing in the corner of the room just to my right.  I could see the edge of a dress, an apron with tools and vials in the pocket, long blond hair curled into ringlets, and that same shroud of smoke around her, moving out to fill the room.  The rest of her was obscured by the wall to my right and the shelves that stood behind the podium.  It put her in an awkward spot for me to shoot.  If I'd known she was there, I would have crawled over to the door at that end, gunned her down at point-blank.



Panacea stood at the far end of the room, at the highest point. She had brown hair that was blowing slightly with the breeze that flowed in through the glassless windows behind her, topped with a flat top cap.  Freckles covered her face, and she was dressed in a tank top and cargo pants.  More than anything else, she wore a look of fear on her face that marked her as the victim, not the threat.



And process of elimination meant the thing beside her was her sister.  I would have called it a coffin, but it was clearly made of something living.  It resembled a massive growth of flesh that had been shaped into a vague diamond shape, gnarled with horny callous and toenail-like growths that protected it and reinforced it at the edges.  On the side closest to me, a girl's face was etched into an oversized growth of bone.  It was unmoving, decorative, with locks of long wavy hair that wrapped around the sides of the diamond.  The `sister' floated a foot over the floor.



It was so startling to see that I nearly forgot what I was doing.  I drew in a short breath, then let slow breath out as I aimed the gun at Jack and squeezed the trigger.



I'd mentally planned to unload the gun on Jack and Bonesaw, but I'd forgotten about the recoil.   At the same time Jack was struck down, my arm jerked up, and my mental instruction to fire nonetheless carried through.  The second bullet hit the ceiling.



I whipped the door open and turned to my right to fire on Bonesaw, but my arm was numb, and her reflexes were sharp.  She was already opening a door at the other corner of the classroom before I could shoot, making her way into the hallway.



I had a split second to decide if I should chase her or go after Jack.  I glanced at Panacea, saw her staring.  As if the eye contact snapped her out of a daze, she lunged toward Jack, one hand outstretched.  She stopped dead in her tracks as he lashed out blindly with the knife.  Reversing direction, she went for her sister instead.



Jack hadn't been incapacitated.  Aside from the impact of the gunshot, he didn't even seem wounded.  He was on his feet in a flash, spinning a hundred and eighty degrees to face me, his knife in motion.



I ducked back through the door, the knife delivering a glancing blow to my back.  It failed to penetrate my costume.



Oddly enough, moving into the hallway and putting my back to the wall made me feel like I'd committed to fighting Jack, even if I might have been in a better position to go after Bonesaw.



``Wake,'' I heard Panacea speak.  She said something else that I missed.



I felt a jolt, but it wasn't physical.  It shook me on an emotional level.  My voice abandoned me, not that I wanted to speak.  I felt as if I stood on the very edge of the grand canyon and any movement, even one to step back onto solid ground, was guaranteed to send me falling to certain death.



The levitating construct of flesh slammed through the door and the door-frame that Bonesaw had used to make her exit.  The mask of bone drew upward like an opened lid, to reveal a clear sphere, containing vitreous fluid and a teenage girl with blond hair.



Her eyes were open, but she looked half asleep, her hair fanned out around her, floating in fluid that seemed thicker than water.  Her arms were outstretched, but her hands and lower body were hidden by the meat that surrounded her.  The edges of the shell that were unfolding around her were curved forward like the horns of a bull.



If the sister had come after me, I wouldn't have been able to fight back.  Like a deer in the headlights, I stood there, unable to think or compel my body to move.



She rotated in mid-air slowly, as if getting her bearings.  As ponderously as she had moved one moment, she went tearing after Bonesaw in the next, slamming through walls as momentum carried her too far and as she turned a corner too tight and sheared through the drywall, tile and window frames.



I could hear Bonesaw laughing with childlike glee as she fled.



``Not smart, not smart, either of you,'' Jack chastised us.  ``See, with Victoria gone, you've left me here with a hostage.''



I stood with my back to the wall, gun in hand.  Ten bullets in here, four spent, if I'd counted right.  I'd always sort of rolled my eyes at how movies treated guns and counting bullets, but it was harder than I'd thought.  The shock and disorientation that came with firing a gun tended to disrupt even basic arithmetic.  I couldn't remember how many times I'd fired during the fight in the parking lot.



``I've been turning every microbe that touches my skin into an airborne plague, Jack,'' Panacea spoke, her voice low.  ``You should be dead now.''



``And me?'' I called out, feeling a pang of alarm.



``I didn't know you were there.  You should be dead too.  Sorry.''



``A benefit of little Bonesaw's smoke,'' Jack answered.  ``If I recall correctly, it's something of a safeguard in case she accidentally deploys a concoction she hasn't immunized herself or the rest of our team against.  The fact that it works against bugs and small rodents is a side benefit, rather than the intent.  Bonesaw's work has made us members of the Nine more or less immune to disease anyways.''



``And the gunshot?''



``Subdermal mesh.  There's more protection around the spine and organs, and you landed that shot pretty close to my spine.  It hurts quite a bit.''



``Skitter!  I don't care if I die,'' Panacea called out, ``I'd rather live, if only to turn Victoria back to normal, but\ldots just don't worry about the hostage part.  If I have to die so you can kill this fucker, I will.''



\emph{It isn't that simple.}  Killing a monster like Jack or Bonesaw?  That was one thing.  I could push myself to do it.  Killing a bystander in the process?  That was something else entirely.



Jack seemed to be able to interpret my pause.  ``I suspect, Amelia, that she \emph{is} worried about the hostage.  The monster that dwells in Skitter's heart is very similar one to yours.  It's a lonely thing, desperate for a place to belong, and the only thing it wants to be brutish to is \emph{her}.''



``Don't pretend you know me, Jack,'' I called out.  ``You already tried to fuck with my head, you guessed wrong.''



``I had bad information.  Cherish has her uses, but she was never going to be a long-term member of the group.  The people who can are truly special.  Bonesaw, Siberian, me.  Perhaps Mannequin, but it's hard to say.  He's not terribly social, but he's been with us for some time.''



I stayed silent.  I could hear his voice changing in volume as he spoke.  Was he moving?



There were two doors leading into the classroom.  Was he moving toward one, aiming to leap out and strike at me?  I glanced down the length of the hall.  Bathroom, janitorial closet, another bathroom, storage room\ldots it made sense that there wouldn't be other classrooms adjacent to a music room with minimal soundproofing.



``You two have your differences, of course.  Amelia, you're burdened by guilt, as you're burdened by your rules and so much else.  I'd like you to think again about how nice it would be to be free-''



``No,'' Amelia's interruption was curt, almost defensive.



``Alas.  Well, while I'm interpreting you two, I'd say Skitter is \emph{driven} by guilt.  What makes you feel so guilty, bug girl?''



\emph{He's trying to distract me}.



I scampered along the length of the hallway, keeping low enough that I wouldn't be visible from the window while I moved to the point just beyond the effects of the bug-killing cloud.  I could send bugs after Bonesaw and the sister -Victoria, was it?- but Bonesaw would still have that cloud of smoke around her.  I doubted my ability to achieve anything on that front.



``There's always \emph{some} guilt related to family.  Tell me, what would your mother think, to see you on an average day?  Or can't you remember her with the miasma?  I'd almost forgotten.''



Even if I couldn't remember her face, who she was, or even where she was, I could feel a pang of regret that knotted in my gut.  I grit my teeth to remind myself to keep from opening my mouth and grasped the cords that my bugs had threaded together.  I looped them around Atlas' horn, and then I ran down the hallway, still keeping low.



Just to check, I tried bringing bugs into the hallway.  The smoke was still present, if thin.  They still died, just a little slower than before.  I returned them to their previous location.  No use wasting them for nothing.



``Skitter,'' he called out in a sing-song voice.  With the acoustics of the hallway, I couldn't pinpoint his location.  ``Aren't you going to reply?''



Just as I was trying to locate him, he was attempting to do the same for me.



I decided to give him what he wanted.



``You're pathetic, Jack.''



I'd intended to provoke him, and I'd succeeded.



I'd also intended to pull the silk cord taut as he stepped into the hallway, tripping him.



Instead of opening the door, he leaped through the open window in the upper half of the door, tucking his knees against his chest.  He landed with a short roll, spotted me, and slashed.



I brought my arms up around my face to protect it.  The feeling of the silk cord's weight dropped to virtually nothing as the slash cut it.



I'd been given tips on fighting, even if I couldn't remember by who or by whom.  \emph{Catch them off guard}.  My arms around my face, nearly blind, I charged him.



He caught me in the side with a kick, but I had enough forward momentum that I crashed into him anyways.  We fell to the ground, and I reached for the smoking vial that hung around his neck.



Jack already had the stiletto in one hand.  He jabbed it toward my face, my eye, and I jerked my head back out of the way, abandoning my attempt to get the vial.  Using one elbow, he shoved me to one side, then flipped over, simultaneously reversing his grip on the knife in his other hand and driving it down toward the side of my head.  I rolled with the momentum he'd given me to escape before it could pierce my ear or my temple.  He was already following up, slashing both knives at me, one after the other.



He knew how to fight, of course.  He'd said he'd been at this for a while.



Hated this.  Hated fighting without knowing enough about my opponents.



I tried to get my feet under me, but it was slow and awkward as I was unable to use my hands.  I had to wrap my arms around my head to shield my face against the continued flurry of slashes. Jack had a knife in each hand now, and he wasn't giving me a half second between cuts, if that.



My forearms and hands didn't cover enough of my head.  I could feel the cuts nicking my ears, slashing through my hair by my temple.  A few slashes made their way through gaps between my arms and fingers.



Blindly, I rushed for the classroom.  Needed a second to breathe, to think, before I was whittled down to a bleeding ruin.  I could hear footsteps behind me.  I felt a hand seize my shoulder.  I whirled and knocked it away, felt another knife slash crossing the back of my head.  I had blood in my eyes, my ears were a bloody ruin, and cuts burned like fire around my scalp and neck.



A shout.  Not Jack's.  I heard it again, the same words, but I couldn't make them out.  There was blood in my ears.



I stumbled into the classroom, and Panacea was at my side in a moment.



``Fix me,'' I gasped.  I couldn't tell where Jack was, and I was hurting enough that I couldn't think to strategize.  He hadn't followed.  ``Fast!''



She touched my forehead, and I could feel the cuts knitting together.



But there was another injury that wasn't mending.



``The red miasma took away my ability to recognize people.  I don't know anything about the people I'm fighting.  Fix my brain.''



``I don't- I can't.''



``If you don't fix me, Jack could win, and \emph{billions} could die.  If you don't cure whatever it is that Bonesaw's done with this miasma, I and tens of thousands of others could die of a degenerative brain disease.''



``You don't understand.  I \emph{can't} cure brain damage.''



My heart fell.



``I- my- the last time I did it, the last time I broke my rules, \emph{everything} fell apart.  You're asking me to do the exact same thing Jack was.  To break my rules again.''



``They're just rules.''  \emph{Where was Jack?}



``They're the only thing holding me together.''



\emph{He's getting away}.  \emph{This stupid girl.}  ``You were willing to die if he took you hostage.  I'm asking you to sacrifice yourself in a lesser way.  Fall apart if you have to.  But undo what Bonesaw's started.''



``This is \emph{worse }than dying,'' she said, her voice quiet.



``Ask yourself if it's worse than the slow, degenerative death of thousands and the potential end of the world.''



She stared at me.



Even as she looked at me, aghast, I felt something awaken in my mind, barriers crumbling.



``This is bad.  Every second is time you're suffering more permanent damage.''



``That's not a huge priority.  I'm more worried about Jack, and all the others who got hit harder by this stuff than I did.''



``It's a parasite that's producing the improperly folded proteins.  I can stop it, and I think I can make them create a counter-agent that counteracts the proteins and promotes healing in the brain.  Can't make them fix the lesions, but I can promote plasticity in the brain and new connections to old information.''



Her voice was so quiet I barely heard it.



But I could remember the others; I remembered Tattletale and Brian.  Rachel.  I could remember Alec and Aisha.  The dogs.  Our enemies.  My dad.  My mom's face popped into my mind's eye and I could feel a relief as I let go of an anxiety that I hadn't been consciously aware of.



``The parasites will replace existing parasites over time, and they'll die if it gets cold, now.  Or if you raise your blood alcohol content.  Get drunk after a week or two to clear them from your system, and don't drink tainted water.  If everyone clears them from their systems, the miasma's effects will be gone by the end of winter.''



``They're probably what she seeded all over the area, before using the catalyst.''



``I'd believe it.''



``And the damage, can you reverse it?''



``The minor damage, yeah.  But I can't do anything for the people with more serious brain lesions unless I attend to them directly.  There's other healers out there, I know they're not as good, but maybe they can do something to fix that.''



I nodded.



Precious seconds passed.



``Let me know the second I can go,'' I said.  ``Jack's going to attack, or pull something.''



``Trying to engineer a large-scale solution to help as many people as soon as possible.  The parasites will leave your body through your sweat, spit and urine, and enter the local water supply to override the others, and anyone you cure will cure others in a sort of reverse-epidemic.  I have to make sure this is engineered right, or nobody's going to get cured.  If I screw it up, it could be worse than what Bonesaw did.''



My leg bounced on the spot with anxiety and anticipation.  Jack was up to something and I was sitting there.



I tried to distract myself with a change of subject, ``Where did you get the material for what you did for Glory Girl?  That sarcophagus thing.  You have to use living material, so\ldots''



``They weren't human.''



``That's not that reassuring.''



``I used pheromones to lure stray cats, dogs and rats to us, then I knit them together.  Victoria didn't have enough body fat to stay warm, and she was wearing out faster than I could get her nutrition.''



``She's going to return to normal, though?''



``Just a little more time.  I have to ensure she's totally together inside the cocoon, then disconnect her from it, and make sure she reaches a physical equilibrium afterward.  Once I know she'll recover\ldots'' she trailed off.



``Amy-''



``Go.  You're done.  Go after Jack.''



I hesitated.  There was a look in her eyes, dark.  She wasn't meeting my gaze.



I turned and ran.  Atlas was waiting on the rooftop as I ascended the stairs.



Too much time lost.  My body was a counter-agent for Bonesaw's prion generators, but I had to find Jack and Bonesaw.  I could scout the area with my bugs, vaguely sense the areas they'd traveled by seeing what spots murdered my bugs on contact, but I still had to track their movements.



Glory Girl was hovering over the school, searching for Bonesaw.  The `cocoon', as Amy had called it, was damaged much as the school gate had been, but Glory Girl was still intact inside.



The fact that she was looking made it very possible that we were facing the worst case scenario.



The bug-killing smoke extended outside of the school gates.  It was hard to verify if they'd gone that way and corked the flow of the smoke or if it was traces from before.  My only resource and means of detecting it was my bugs, but testing it meant killing them by the dozens, if not hundreds.



If they stayed on the grounds and I left, it could mean something ugly for Amy and Glory girl.  Conversely, if they'd left and I stayed, it could mean disaster for \emph{everyone else}.



I left, flying Atlas in an ever-expanding circle, reaching out with my bugs to scan the surroundings.



With a mixture of relief and fear, I realized that Bonesaw's extermination smoke was stronger a half mile away.  I'd been lucky enough to guess right.



They'd split up.  Two trails, extending down different streets.  My bugs felt around to see where the death-zone was, a few dropping dead each time, their numbers whittling down.  It was like a game of battleship, with constantly moving ships and limited ammunition.



Three trails.  I stopped in mid-air.



\emph{Three?}



I gave chase to the nearest one, abandoning Atlas to pursue the subject into an alley, through a hole in the wall and into a derelict building, past a pile of rubble\ldots this wasn't right.  It was too nimble, moving through spaces too small for even Bonesaw.



And before I even returned to Atlas, there were a half-dozen trails in total that were branching out around us.  In another few minutes, there were a dozen.



Our group had used this method some time ago, using Grue's power to slip away from the bank robbery.  But how were they doing it?  It wasn't just the wind carrying the gas down misleading alleys.  Were there living creatures carrying vials of the stuff?



\emph{Mechanical spiders}.  They'd found their maker, and Bonesaw was using them to distribute the vapor and cut off my swarm sense.



They'd escaped.





