





I continued my search for the pair, but my tentative explorations of the trails of extermination-mist made a sweeping search all but hopeless.



It felt like I was facing a series of decisions where every answer had some merit, but picking the wrong one would spell disaster.  I'd had to make the call between staying at the school in case Jack and Bonesaw were preparing a trap for Amy and Glory Girl, or leaving in case they'd made a run for it.  I'd left, and I'd been lucky enough to be right.



Except the Nine were now covering their tracks with a dozen decoys, mechanical spiders leaving trails of bug-killing smoke, leaving me to guess which direction they'd gone.



Two solid possibilities dwelled with me.



The first was that they'd headed back downtown to rendezvous with Siberian.  If I was drawing the right conclusions from what I'd overheard, Bonesaw had drawn together a cocoon for Siberian similar to the one that Amy had created for Glory Girl.  They could be recovering her real body, maybe doing something to recover Mannequin or Crawler.



It hadn't even crossed my mind while I was under the miasma's influence, but I also had to wonder whether Regent would have maintained his control over Shatterbird.



The second possibility was that they'd gone after Cherish.  My conversation with Coil had clued them in.



I checked my phone.  No service.



\emph{Damn} the Director.  Damn her for making this so hard, and for complicating matters.  We'd been playing by Jack's rules, more or less, and she'd given him an excuse to pull out all the stops.



He probably would have anyways, but she gave him an excuse.



If I headed away from the downtown area, toward the water, I could put myself in a position to track down Cherish, or to get to another point where the satellite phone would work and make a call to Coil.  If they were checking the harbor for Cherish, going by what she'd revealed on the phone, then I could get there first.  Lay a trap, or get in position to shoot them again.  I figured out how to remove the magazine from the gun and checked the number of rounds remaining.  Six.



The problem was that the whole reason I'd let Panacea keep using her power on me instead of giving chase to Jack was that I was supposed to cure the others.  I could kill and replace the parasites that were carrying the prions.  The sooner I did it, the less damage they'd do in the meantime.  Some of the damage would be permanent, and the potential victims included Brian and Lisa.



I \emph{wanted} to head back downtown, to help my teammates and friends, but I couldn't shake the nagging doubt in the back of my mind.



The difference between Jack and Bonesaw going downtown and their going to the coastline was that the former was almost kind, taking care of a teammate.  The latter case allowed them to inflict some terrible torture on an ex-teammate of theirs.



It was the most inconvenient possibility, but my gut told me they'd go after Cherish.  If I had to put numbers on it, I'd have said there was a sixty percent chance they'd go that route, a thirty-five percent chance they'd headed downtown.  And there was always the possibility I was wrong, that they had something else in mind, so I was leaving room for that extra five percent.



But if I was wrong, if I went to the harbor to try to get ahead of them and Jack didn't go that way, then my friends would suffer for it.  Brian had been through enough, and while Lisa had seemed to deal okay after she'd been scarred, I was willing to bet she valued her mind more than she valued her face.



I headed downtown.



No matter which way I chose to go, I'd have that awful feeling of regret in my chest.  I tried to quiet it by telling myself that with Tattletale and the others, I'd actually be able to \emph{do} something against the Nine.  A gun and knife didn't cut it, no matter how scattered or few in number they were.



I couldn't quite manage to convince myself.



As it didn't cost me anything significant in terms of forward momentum, I let Atlas carry me higher.  I was getting more comfortable flying him, and there was little difference in being a hundred and fifty feet above the ground and being five hundred stories up.  I wanted to assess the situation.  Was my dad one of the people who was depending on this cure?



The topography of the city had impacted where the miasma was spreading.  As far as I could tell, it wasn't really advancing into the north end of the city.



Bakuda's bombing campaign and the militarization of the ABB had predominantly focused on the Docks.  Leviathan had arrived in the Docks, and his destruction of the city's water infrastructure and power had hit that part of the city hardest.  I wondered if this would be the first real instance where the Docks weren't hit as hard by the ongoing series of disasters and attacks in Brockton Bay.



I descended back to a safer distance, where falling \emph{wouldn't} be terminal, and tried to plan.



Finding Tattletale was number one.  With her assistance, everything else would be easier.  As much as I wanted to make Grue my second priority, I knew that there were other things that took precedence.  Siberian was a big one.  Finding a way to distribute the cure was another.  Once I started, it would set up a chain reaction, but I had to decide how to start it off.



Tattletale first.  She could help me find Siberian and figure out how to distribute the antidote.



I tracked the trails of extermination smoke as I flew.  I was faster than they were, but they were elusive, staying out of sight and moving through awkward positions.  I spotted one mechanical spider moving through a trash-littered alleyway and changed my route to close in on another trail.



My second confirmation of a mechanical spider left me with the feeling that I'd made the wrong call.



But it was too late to turn back.  It would be faster to go help Tattletale and get her assistance than to turn around and fumble along on my own.



They were traveling on foot, I hoped, and they still had to \emph{find }Cherish.  She was bound to be in a remote spot, and they didn't have many clues to work with.  It would take time.



Things hadn't exactly been quiet while I'd been gone.



``Calm down!  If we all just stop fighting, then this doesn't end in tragedy.''



``Why should I believe you?''



``I'll tell you as soon as I can think of a convincing reason!''



Tattletale was on the street, alone, facing down Bitch, two dogs and one wolf on full-tilt mutation-mode.  They advanced with measured steps, keeping close to their master.



I landed beside Tattletale, and the two of us made eye contact.



``L-mist.''



``A-Carnelian,'' she answered.  ``You understand if I don't trust you implicitly, here?''



``I do.  Listen, I've got a cure-''



``Who the fuck are you!?''  Rachel shouted.



I shut my mouth and turned to face her.



I was secretly glad the dogs hadn't turned on her, as that probably would have meant the death of a teammate, but I was getting a firsthand look at what our enemies had to deal with.  The dogs were big and vicious enough that if they attacked, there wasn't a whole lot I could have done.  Heck, Tattletale and I together couldn't have managed much of a defense against \emph{one }of the creatures, let alone three.



``We're teammates,'' I told her.  ``I was just fighting the Nine, I've got a cure for this thing.''



``Or you're going to kill me the second I let my guard down.''



I'd been conned by the Nine.  Tricked into letting them get access to certain information.  Bitch wouldn't have fallen for that, but that came with the caveat that she was that much harder for \emph{us} to reassure.



``I can put my weapons away.  Or give them to you.''



``I'm not that stupid,'' she growled the words.  ``Don't treat me like I'm retarded.  I'm not.  I know you have powers.''



``That wasn't what I wanted to say,'' I said.  I kept my voice low, my tone as calm as I could manage.  ``I was just saying I'd disarm myself if it would reassure you.''



``The only thing that's going to make me feel any better is getting the fuck away from here.  But \emph{she} wouldn't get out of my way.''



``If you leave,'' Tattletale told her, ``You'll go straight to the Trainyard, to your other dogs, and you'll get \emph{worse}.  You'll wind up isolated from the rest of us.  And I think the Nine want that.  They wanted people for their group, and doesn't this set their candidates up for easy recruiting?  Separate them from their previous attachments, leave them vulnerable and lost, then give them the hard sell.''



``Not that you're wrong,'' I said, glancing at Tattletale while trying to keep the dogs in sight, ``I saw Jack trying that with Panacea.  But Bitch tends to see it as slimy or conniving when someone talks a lot.''



``I see.  You want to try, then?''



Bentley growled.  It didn't sound like a dog growl.  What worried me, though, was Bastard.  He was untrained enough that he wouldn't necessarily listen to Bitch, and big enough to feel confident about attacking.



Not that I was positive she would \emph{stop} him if he attacked.  As much as she felt like she'd feel more secure on her own, Bitch might well decide she could resolve this situation by killing anyone who threatened her.  It wasn't that she was the murdering type, but she didn't have the innate sympathy for her fellow humans.  She cared as little about murdering us as I might feel about killing two dogs if I felt like my life was on the line.



I'd been in a similar headspace, trying to figure out who was friendly and who wasn't.  Jack had been more on the ball than I, and I'd fallen for his ploy.  I'd deal with the guilt over what that might mean at a later point.



``A little while ago, we spent some time in one of your shelters.  I'm guessing you don't remember who, but you remember chilling out and eating Greek food with someone?''



``You could have found that out through someone else.''



``I know.  That's not what I'm saying.  I'm just wanting you to think about that feeling.  I'd like to think we got along, as far as people like you and people like me can get along with others.''



``Doesn't mean anything to me \emph{now}.''



``Okay.''  I let my arms drop to my sides.



``That's it?  That's your argument?''



``I don't really have much better.  I know that if I tried to convince you using logic and a well worded argument, you'd feel like I was being manipulative.  All I can say is that we had a good time then, we were friendly.  I know we parted ways some time after that, but I'd \emph{really} like to get back to that point.  So I'm appealing to that emotional attachment, I guess.''



``You think I'm attached to you?''



\emph{This again}.  This situation seemed to be highlighting the worst parts of people and twisting others.  Amy's paranoia, Legend's battle instincts, Bitch's antisocial tendencies, and my\ldots whatever it was, that led to me trusting Jack.



``Yeah.  I'm making that assumption,'' I told her.



``Fuck you.''



She advanced, and I stayed put.  Sirius growled.



``I'm not your enemy,'' I said.



``We'll attack you.''



``If you do, maybe the cure will get transmitted to your dog, and then to you.''



``You're not that stupid.''



I shook my head.  ``Not really.  But I don't think you'll attack me, either.''



She advanced closer.  Sirius growled again, and she held one hand out to stop him.



\emph{So glad they still listen to her}.  This would be a disaster if the dogs were on a rampage.  I supposed the miasma was slower to affect them, given their mass, or the vectors it affected weren't present or as predominant in dogs.



She stepped close, until her nose was an inch from mine.  She stared unflinching into my eyes.  I met her gaze with that same unforgiving hardness.



``No way I could like someone like you.''  The words were like the twist of a knife.  Hostility and aggression combined with pure, petty malice.



``Just going by looks, when you can't see half my face?'' I asked.  Without breaking eye contact, I reached up and pulled down the lower half of my mask.  ``You don't recognize me?''



She didn't glance away from my eyes.  ``No.  Now move.  I \emph{will} order them to attack.''



\emph{She would.  She could}.



I leaned forward and planted a quick kiss on her lips.



Her punch knocked me off my feet and sent my glasses flying off my face to land in the water somewhere nearby.



``The fuck!?''  She shouted.  One of the dogs growled, deep, as if to complement her anger with a threat of his own.



``You're cured,'' I told her.  ``That's it, that's all it takes.''



She stared down at me.



\emph{If this doesn't work, she might kill me for real}.



Tattletale helped me to my feet and handed me my glasses.  I got my mask in place around the lower half of my face and then gathered bugs over the mask and glasses to hide my features.



``How's that work?''  Tattletale asked.



``The effects are being generated by a parasite.  Panacea changed the parasite to some kind of symbiotic species that overrides the effects of Bonesaw's work and heals the effects on the brain.  My bodily fluids are carrying it.  That means that right now, the parasites in Bitch's bodies should be dying or getting replaced or transformed or something.  I hope.''



I dusted myself off, wiped at my costume where I'd landed in the water, and made sure none of my belongings had dropped from their positions in my armor or my belt.



I didn't hurry to meet Bitch's eyes, because I knew that when I did, I'd have to maintain that gaze.  Only when I was done did I meet her eyes.



She took her time responding.  ``I was going to have Bentley break you.''



\emph{It worked}.



``Glad you didn't.''



``Why?''



Why had I done it?  I'd tried to explain it to her so many times.  I couldn't bring myself to do it again.



``Doesn't matter.''



Tattletale pointed down at the water just behind me.  I turned around and looked.  Where I'd landed on my back, the water was changing from red to a relatively clear state.  `Relatively' only because the water hadn't been that clear to begin with.  ``Guess it's working.''



``Good,'' I said.  The last swirls of red disappeared from around my feet, and the water around me began to change back to normal.  With increasing speed, the water around us began to transition back to normal at nearly the speed the effect had spread in the first place.  It extended out in every direction, promising to revert most or all of the affected bodies of water.



``You couldn't have waited until after you'd cured me before you put the bugs on your face?''  Tattletale asked.  She was smiling as she asked it.  ``Unless you want me to drink that water.''



``Sorry.  No, I'll help you out.''



She gave me a stern look, pointed at me, and said, ``No tongue.''



I rolled my eyes, scattered the bugs, pulled my mask down and leaned over to give her a quick peck on the lips.



``Now fill me in.  I'll fill in the blanks as you explain, and hopefully it'll work fast enough that I can catch up.''



``Jack and Bonesaw tricked me and Coil to figure out where both Cherish and Amy were.  I gave chase, and Jack left before he accomplished anything more than head games.''



``State she's in, head games are pretty serious.''



``Maybe.  But at least she didn't cave on his demands.''



``Sure.''



``The bad thing is\ldots Jack knows about Dinah's prophecy.''



Tattletale looked as though I'd slapped her.  ``\emph{Shit}.''



``I mean, her numbers weren't that good as far as our mortality rate going up against the Nine, so maybe she's wrong about-''



I stopped as Tattletale shook her head.



``Depends how you interpret it,'' she said. ``The kid sounded pretty certain.  Anyways, keep going.''



``Siberian's somewhere downtown, her real body in some kind of case, maybe.''



``I think we might have run into her,'' Tattletale said.  ``I wasn't paying a lot of attention to details, mostly just trying to avoid trouble.  But I'm pretty sure she was hauling around something big.  Fuck, I think she might have had a friend.''



``A friend?''



``Hookwolf.''



I nodded slowly.  ``Where was she headed?''



``North.''



``Where did Coil stick Cherish?''



Tattletale made a face.  ``North.''



If there had been a wall in reach, I would have punched it.  ``Wonderful.''



``Explain?'' Bitch asked.



``They're heading over to Cherish's location, I'm almost a hundred percent positive,'' Tattletale explained.  ``If Siberian's heading there to rendezvous with them, then any further encounters with them are going to be ugly.  Doubly so if they have new blood on their team.''



``Hookwolf's under the influence of Bonesaw's miasma,'' I added.  ``Don't know what his reasons were for staying here, but the miasma seems to have eliminated that.  He's with the Nine.  Maybe permanently.  Bonesaw will keep it from killing him, I guess.''



``So they got their candidate?''



``And,'' I addressed Bitch as I spoke, ``They might be looking for more candidates to round out their group.  If they left Siberian behind to try to recruit Hookwolf, and they tried a pretty aggressive strategy against Panacea, then they might make another stab at recruiting you.  Or Regent.''



``Or Noelle,'' Tattletale added.



Why did that give me such a bad feeling?



I sighed.  ``Let's hope it doesn't come to that.  I think we should give chase.''



``Head to where Cherish is?''



I nodded.  ``It hasn't been too long, so they won't have much time to prepare any counterattack.  It does still leave the problem of finding the others and curing them before something bad happens.''



``If the cure is contagious\ldots  Bitch, you think you could work on finding and curing the others?''



``How?''



I spoke up, ``Cure your dogs.  Spit in their mouths, whatever.  Then see about tracking down the others, ambushing them, and having the dogs lick their faces?''



She scowled.  ``I haven't trained 'em to do that.''



``You've got ten minutes to teach them,'' Tattletale grinned.



``Whatever.''



``You'll see about curing the others?''



``Yeah.''  Bitch pointed, ``But it won't work with my dogs.  They kill any parasites while my power's working.''



\emph{Right}.  I could remember curing Sirius of heartworm.



I shrugged.  ``Another way?  Maybe if you dose some fresh water with the new parasites, spit in it, then splash people?  People are going to start getting better fast, with the water changing, but let's make sure our side is okay?''



Bitch nodded once, curt.



``And can you loan me Bentley?''  Tattletale asked.



``I'm starting to wonder why I'm on this team,'' Bitch grumbled.



``You have to ask?'' Tattletale grinned as she approached Bentley.



``I know it's just words,'' I told Bitch, ``But I'm glad you're back.''



She stared at me like I was speaking Klingon.



``Let's go,'' Tattletale said, as she climbed onto Bentley.  He growled, but she didn't seem to mind.  Maybe his bark was worse than his bite and she knew it?



Either way, I decided to trust her and took off.



I'd done my part, and I'd have to trust Bitch to complete the task.



I was making more forward progress than Tattletale, though I could feel Atlas fatiguing.  It wasn't the same as the fatigue I experienced, but he was slowing down fractionally in his wingbeats per second.  It stood to reason.  He was big, and he hadn't eaten since he was created.  That was compounded by the fact that he'd been going full-bore with minimal chance to rest.



Still, we had the advantage of being able to fly \emph{over} obstacles, which was something I was gaining a greater appreciation of since I'd gotten the hang of flying him.



With Atlas being tired, not wanting to lose track of Tattletale, I kept our flight close to the ground.



``Where is she?'' I called out, as I met her pace.



``Boat Graveyard.  Beached ship, she's in the hold.''



``Coil told you this?''



``No, but he'll forgive me for figuring it out, given circumstances.''



``If you're sure.''



It wasn't a short trip.  Our destination was north of the market, and the market was a distance from my house.  We were making our way from downtown to the Boat Graveyard.



When the local industry had collapsed, the Boat Graveyard had been something of a staging ground for the irate dock workers.  Shipping companies based in Brockton Bay saw the signs of what was coming and trapped other boats in the harbor as a form of protest, to ensure they weren't walking away empty-handed.  Police had made arrests, but actually moving the ships out of the way required sailors, and the move had mobilized enough of them that clearing the upper areas of the docks of the ships became all but impossible.  Things capped off with fights, gunfire and a deliberate sinking of a container ship by one of the protesters.



Opinions varied on whether the incident had been a symptom or a cause of the collapse.  Either way, the result was the Boat Graveyard- an entire section of the coastline where boats had sat for so long that they'd rusted or taken on water.



We paused at the top of a hill overlooking the scene: forty or fifty derelict ships, some bigger in sheer mass than the skyscrapers downtown.  Leviathan's waves had slammed them all into the coastline, smashing them against one another and turning more than a few into something unrecognizable.



Even with Tattletale's hint, I wasn't sure I could have found where Cherish was lurking.



``How do we find her before she finds us?'' I asked.



``We don't.  She knows where we are.''



I scanned the wreckage with my eyes.  Would Siberian pop out?  Hookwolf?



``They aren't attacking.''



Tattletale shook her head, but she didn't speak.



My bugs began searching for signs of life.



``You outrange her,'' Tattletale spoke.  ``You detect them, you attack before she can whammy us.''



``Yeah.''  \emph{Fat lot of good it'll do with Siberian there}.



I was getting a sense of why there wasn't any foot traffic here.  Even on land, the force of Leviathan's tidal wave had sent age-worn sheets of metal flying over the landscape.  Ragged edges of rusty sheet metal waited under every step I took, scraping and stabbing against the soles of my costumed feet.  Tattletale was relying on Bentley's weight and durability to handle anything that waited underfoot.  He was still panting hard from the run.



My swarm sense alerted me to life in the hold of a ship.  The space was half-filled with sand, and water had leaked in through a hole in the side of the ship.  If supplies were delivered by way of remote control, that was a likely route.



Seven people.  Three male, four females, one of whom was young.  A child, long-haired.  That would be Bonesaw.



``There?''  I pointed at the location.  It was barely visible from where we stood; two ships had been slammed against one another, nose to nose, and they formed a precarious arch over the ship in question.



``Yeah.''



``I've found them, I think.  I think Siberian's there.  There's a lot of people, anyways.  Seven.''



``How much damage do you think you can do?''



``Not enough.''



We paused.



``Cherish should be alerting them,'' Tattletale spoke.  ``I'm surprised they aren't mounting a counterattack.''



``Maybe they can't?  If they split up, Siberian won't be able to protect everyone,'' I said.



``Well, getting closer is a pretty bad idea.''



``Do we have a choice?''



``We hang back, we follow them, we strike if we spot an opportunity.  Between Bentley and Atlas, we can keep at a distance.''



I shook my head.  ``Bentley's tired, and I don't know how long Atlas is going to be able to keep flying.''



``They'll manage.''



``You sure?''



``Pretty sure.''



\emph{Pretty sure}.  So she wasn't \emph{positive}.



``There's another possibility,'' she ventured.



``Do tell.''



``Cherish might not be saying anything because she \emph{wants} us to attack the others.''



``Or,'' I pointed out, ``The Nine are giving us that impression because they want us to think that so they can turn the tables.''



``That line of thinking leads to madness.''



``Call me crazy, but I'd rather not gamble.''



``So?  What's the plan?''



``We wait?  At least a little while.''



``Sure.''  She gave the bulldog a pat on the head.  ``Give Bentley a chance to rest.  You can feed Atlas.''



``Pretty narrow window of time,'' I added.  ``Bitch's effects on the dogs don't last that long.  Figure twenty minutes, and we took at least fifteen to get here\ldots''



``But she gave them more juice than usual.  I'd say roughly ten minutes before he's too small to carry me,'' Tattletale said.



``Ten minutes.''



We settled into a position behind cover, and I began drawing bugs to me to feed Atlas.  I wasn't positive about his diet, and Grue had said that he'd given Atlas a more human digestive system, which left me uncertain.  That said, Atlas was made of bugs, I figured he required the nutrients they provided on a sheer logical level, like how humans would generally get most of the nutrients they needed by eating other humans, if they had to.  That, and I'd pointed out to the rest of the group how bugs were something \emph{we }could eat as humans, so his digestive tract could probably manage them.



It was also the easiest thing to provide.



``You have eyes on them?''



``Minimal.  My interpretation via the swarm's eyes and ears is still garbage, as always.  And I didn't want to have so many around them that they get suspicious.''



``Can't make out what they're saying?''



I shook my head.  Still, I \emph{could} tell that they were talking.



Seven of them.  One of the men was garbed in smooth body armor that covered everything.  Mannequin.  There was another man who could have been Siberian's real self or Hookwolf.  Long haired, shirtless.  My bugs traced the edges of knives at one man's belt: He was the quietest, and was pacing without cease, sitting down, then pacing again.  Jack.



Three women, none of whom were Siberian if I accounted for the presence of clothing and the texture of their skin.  Rounding out the group was a little girl with long hair.  One of the women was doing most of the talking.  Would that be Shatterbird or Cherish?  Who was the third?  Had the Nine gotten their hands on Noelle?



It unsettled me that Jack wasn't taking more of a lead in the conversation.  Maybe Cherish was just dishing out the dirt?



``The dynamic seems wrong,'' I said.  ``Something's off.  Not sure if Siberian's present or not, Bonesaw's quiet and Jack is mute.''



``Maybe Cherish took control?'' Tattletale ventured.



It was a scary thought.  The Nine were strong, and one of the only reasons they weren't a bigger problem was that they were their own worst enemies.  Most of our victories to date had been because we exploited their character weaknesses.  Under a leader\ldots



``No.  Bonesaw took measures.''



``Maybe Cherish found a way around it?''



I didn't have a response for that.  Minutes passed, and the Nine lapsed into silence.  Some were resting.  Or pretending to rest.



``They're napping or something,'' I said.



``Could be baiting you.''



``That's what I was thinking.''



``And Bentley's getting too small to help me make an exit.''



``Atlas can manage with just me,'' I told her.



``Going alone?  No.  Grue would kill me.  It's senseless.  I can call Coil, so we can get a squad of soldiers in place to try and take someone out.  Or maybe we get the Director to bomb the area.''



``Because that's worked so well this far.''



Tattletale smiled a little.  ``What would you rather do?  Going in is suicide.  You'd be opening yourself up to Cherish's power.''



``She's resting.''



``You think.''



``Not sure which person she is, but her breathing is really regular, has been for a while.''



``And she could be faking it, a hundred percent aware that you're thinking what you're thinking.''



``Yeah,'' I admitted.



``Why are you so fixated on this?  On going in?''



``I want to end this.''



``That's not your real reason.''



``And I feel like something's wrong.  The details don't jibe.''



``That's a less than stellar reason to put yourself at that kind of risk.''



``There's a chance Siberian isn't here, or isn't in a state to defend her allies.  But\ldots I can't bring myself to attack.''



``This is a shitty time to have an attack of conscience.''



``You sound like Jack.  He tried to push me to kill while I thought he was Grue.''



``You'll have to explain how all that happened at a later date.  Jack's good at fucking with people's heads.  It could still be a trap.''



``It could.''



``But?''



``I've got this feeling in my gut, like I had when I was around Jack and Bonesaw, and I wish I'd trusted it then.  I don't want to doubt it now.''



``A gut feeling?''



I nodded, once.



She sighed.  ``What can I do?''



``Get out of here.  I don't want to hurt you if I fall under Cherish's control, which is supposed to be pretty short-lived.  In case she plans to make it more long-term, maybe call the PRT director and arrange a firebomb if I don't report back?''



Tattletale made a face.  ``This is dumb.''



``I've done dumb things.  I somehow don't feel like this is one of them.''



``Go, then.  Call me as soon as it's safe.''



I nodded.



She headed out of the graveyard with Bentley.  I waited a few minutes, until she was out of my power's range.



Atlas and I crossed the gap to the ship.  I waited for the hit of Cherish's power, but it didn't come.



My bugs sensed more of Bonesaw's traps – areas heavy with fog, or where vials had been thrown, placed or dropped.  I was glad there wasn't any of the extermination smoke.  I set foot on the tilted deck and began slowly making my way into the ship.  My soft soled costumed feet were quiet, barely audible to myself.



I drew my gun, readying myself to fire the second I was in range.  If Cherish was setting up the Nine for me, I was pretty sure I could hit one and get away before trouble arose.  It was a feeble thought – even Jack, one of their most vulnerable members, hadn't fallen to gunfire.  Still, it was reassuring.



More traps forced me to make slower progress through the labyrinthine ship's interior.  It was a while before I could stop at the outside of the door at the lowest point of the ship.



I heard sobbing.



I stepped through the doorway and took in the room's interior.



The floor sloped one way.  Half of the room was metal flooring covered in sand, the lowest half was submerged.



Three men, three women and a girl.  The man with knives in his belt stood, then began the ritual pacing once again.  His feet were raw where the rusted metal deck had cut at them.  The others sat and stood in various points around the hull.



I withdrew my phone and called Tattletale.



``That was fast.''



``It's not the Nine.  Decoys.''



I stared at them.  The disguises had been rushed but thorough.  Jack and Bonesaw had clearly changed clothes with the people in question, and Bonesaw had whipped up something approximating Mannequin's armor for one of the men.



``Call Coil, get medics here.  It's Bonesaw's work, so he might need to call on some expert surgeons to undo whatever she did.  I'll use my bugs to mark out the traps that Bonesaw set up inside.''



``On it.''  She hung up.



\emph{Paralysis, compulsive movements}.  Puppets.  Decoys.  Had this been Jack's attempt to make me betray my morals?  Setting up decoys with the idea that I'd attack first and check later?  If I'd gone with my first impulse and tried to kill them, I'd have seven civilian deaths on my hands.



``Help is on the way, guys.  I'm sorry about this.''



``Thank you,'' the twenty-something woman I'd guessed to be Cherish spoke.  The others were mute.



I saw drag marks in the sand, leading to the water.  Who had that been?



The knife was the last thing I spotted.  It had been slammed into the metal hull of the boat.  I stepped over the chain and collar that had probably been attached to Cherish.  I pulled the knife free of the wall and used my bugs to catch the note before it fluttered to the floor.



\emph{We concede our loss to you, Brockton Bay.  As per my agreement with Miss Amelia, we'll be leaving your fascinating city.  It was fun.}



\emph{Don't worry about Cherish.  She's sleeping somewhere at the bottom of the bay.  Bonesaw was kind enough to crank up her receptive range toward negative emotions and remove her filters.  The girl will personally experience every awful feeling Brockton Bay's inhabitants do- and with the benefit of Alan's tech, she'll get to do it for a very, very, very long time.  }



\emph{A departure marked n}\emph{ot with a bang, but a whimper.  I'm sure you understand.}



\emph{Yours truly, }



\emph{Jack.}





