





``Lift!'' Sierra grunted.



The tightness in her back was reminder enough to use her legs to rise to a standing position.  Her hands were blistered and every knuckle was scraped or bruised.  They were carrying a door, torn from its hinges; the peeling paint, the worn wood, and the weight of their burden made it less than comfortable to hold.



She held one end of the door.  Jay was at the opposite end, his back to the man who was draped over it.  She wanted to ask Jay to hold the other end; she doubted looking down at the figure as he carried the makeshift stretcher would even bother him.



But she didn't ask.  She couldn't spare the breath.  They'd been working so long already, it was easier to forge ahead than to stop for any reason.



Still, her silence meant she was faced with the corpse of the man who had once lived here.  Once upon a time, he'd had parents, had a first day at school, had made friends, even had a crush on someone.  He had probably worked.  He'd had things he loved about life, no doubt, and if he was living \emph{here}, he probably had more than enough things about life that he'd hated.  Whoever he'd been, he was another one of Mannequin's victims now.  Not quite so disturbing as the ones killed by Burnscar.  He didn't have a wallet on him, so he was a John Doe for now.



When they'd started working yesterday, that sort of thinking had made her want to cry.  Now she felt numb.  She could have thought about something else, but a part of her wanted to pay John Doe his due respect.  If nothing else, he deserved to be looked at as a human being rather than another body.



She bent down to set the door on the ground.  Jay took hold of the man by the shoulders, she lifted by the pants legs, and they moved him three feet to the right.  John Doe was set down on the concrete floor.  He joined twenty-nine other bodies, now arranged in two rows of fifteen people.  Too many were fellow John and Jane Does.



A blister had popped on her hand as she'd carried the door.  It smarted, but her focus was on the man.  Forty or so, but the yellow of his skin pointed to liver problems.  He could be as young as thirty, prematurely aged by alcoholism; it wasn't like she hadn't seen enough drunks around the city to be blind to the signs.



She felt like she should say something, but the words didn't come to her.  Had he been a mean-spirited lecher of a drunk?  Someone who'd worked hard at whatever job he could find to support his family, then drank his worries away with his buddies after a shift?  A lonely man without anyone to care for him?



She considered a simple `sorry', not necessarily because she felt guilty.  She was speaking more for the fact that she couldn't do more for him, and apologizing on behalf of the random, senseless events that had taken his life.



``Next?'' Jay asked.



She looked at him.  He was tired, but she didn't see any signs of the same emotional drain she was experiencing herself.  He'd been a gang member in the ABB, had preyed on others, maybe even killing.  This job didn't faze him in the slightest.  Behind his shaggy hair, his narrow eyes were cold, uncaring.  He could have been carrying groceries for all he seemed to care.



It creeped her out.



``No,'' she said.  ``I've hit my limit.  Can you find someone else to move the last two bodies from the factory to here?''



``Okay.''



She stared at the bodies.  Hopefully they could arrange something early in the morning.  Maybe if she put together a group and sent them downtown to verbally request help?  It was only one of a growing number of issues she was having to solve.  She sighed.  ``I'm going to go see how things are inside.''



``Okay.''



She watched as he left to rejoin Yan and Sugita, the other two ex-ABB members.  He must have said something to them, because Yan turned to look at Sierra.  The look was intense.  It wasn't jealousy from the Chinese-American girl.  It was something else.  As creepy as Jay was, his girlfriend's stare scared Sierra more.



Exhausted and unnerved, Sierra headed back to Skitter's headquarters.  She double-checked that nobody was following before entering the storm drain.  It was pitch black inside.  Humid.  She walked with fingertips tracing the right-hand wall.  When that wall ended, she kept walking.  It was disorienting, uncomfortable, walking without a guide in darkness so absolute she couldn't see her hand in front of her face.



She felt the wall again, and she kept her hand on it as she rounded the next corner.  There was a wet patch where some small amounts of water were trickling down from the street above\ldots two more paces, then a left hand turn.  She fumbled around briefly to find the opening.



That was the hardest part.  The rest was easy – finding the doorway, entering the cellar, then heading upstairs to the main floor.  She was glad to see light, to let go of that fear that she'd miss the gap and find herself wandering the storm drains and getting lost, unable to find a way back to the surface or the beach.  She wondered if Skitter had felt the same way.



She nearly tripped over a small child as she made her way into the kitchen.  Charlotte was there, and she was busy emptying the cupboards.  Everything edible was on the counter or on the floor, neatly arranged.  Sierra estimated roughly twenty children were on the ground floor.



``There's more than there used to be.''



``O'Daly clan.''



Sierra frowned.  ``They need to take care of their own kids.''



``They're kind of preoccupied.  They were hit harder than anyone else by the attack.  I think only six of the twenty who were with us are left.''



``I know.  But they still need to take care of their kids.''



``Give them one more day to mourn?''  Charlotte asked.



``It's your call.  You're the one babysitting in the meantime.''



``I'm trying,'' Charlotte said.  ``But they're switching between playing and being pretty normal kids to crying because their parents are\ldots you know.''



\emph{Dead}.



``Yeah,'' Sierra confirmed.



Charlotte had taken off her mask and was using it to tie her hair back.  She straightened it and tied it over her forehead again.  ``Isn't the city supposed to handle this?  There should be something like foster care, or a special evacuation plan for orphaned kids.''



``I don't think the city knows.  It's not just the kids.  We've got thirty dead bodies and it's not exactly cool out, and there aren't any ambulances or anything showing up to handle it. We just spent the entire afternoon moving them to a new spot with Jay and two locals.



We were talking about burning them in a mass grave, but I'm worried that's against the law.  And since half of them don't have ID, we might ruin any chance of their families identifying them.''



``Not easy.''



``No,'' Sierra admitted. ``How's the rationing?''



``It's less like she went shopping and more like she wanted to stock this place like it was a miniature grocery store.  A little bit of everything.  I'm trying to organize it by expiry date so we can prioritize eating and serving the food that's going bad now, in case she never comes back and the food starts to get low.''



``I know it's a bit late, but there's a lot of us who've been working hard, cleaning up the mess from the attacks\ldots''  Sierra hedged.



``You want dinner?''



Sierra pressed her hands together in a pleading gesture.



``Maybe soup?  I figure we need to eat these vegetables, there's stock, and if we water it down so we can split it up more\ldots''  Charlotte trailed off.  ``I never really cooked at home.  I helped my parents cook, but that's not the same thing.''



``It works.  Prepare some rice from the supplies, since we have more than enough of that.  Bulk it out.  We have a lot of mouths to feed.''



``Okay.''



All she wanted to do was stop.  Instead, she stepped into the living room, where makeshift beds had been arranged with piles of blankets and sleeping bags.  Only two kids were sleeping there, both clearly brother and sister.  It was as much privacy as she was going to get.  She plucked the satellite phone from her pocket.



This scenario wasn't what she'd expected, on any level.  Even as Skitter had explained the job duties as being helping out, rebuilding, organizing, Sierra had maintained doubts.  She'd been waiting for that \emph{one} job where Skitter tested her limits, asked her to do something a little dangerous, something morally ambiguous.  It would be subtle, or it would have consequences she wasn't immediately aware of, but it would set her on the road to something darker.



Except it hadn't happened yet.  Even the scope of what she was doing here caught her off guard.  There were innumerable dead, and yet more people forced out of their homes by the fires Burnscar had started.  It seemed like everyone was walking a narrow line between banding together as a community and killing one another.



It felt strange to identify as one of the key people who were pulling for the former.  She was organizing everone, keeping in touch with the groups handling the other cleanup jobs and working tirelessly at the hardest and most unwanted jobs in the hopes of inspiring others to keep going.  When the smell of shit and rot that accompanied the dead got to someone, Sierra was at their side, helping calm them down, always ready to name another place where they were needed.



It was almost too much.  A huge part of her wanted to call Skitter, to get some guidance, to order supplies and defer on the harder problems, like the bodies.



Another part of her was scared to.



She dialed another number instead.



``Yes?'' the voice was deep.



She was put in mind of being a little kid, calling a friend and hearing an adult on the other end.  It felt awkward.  She sort of resented it.



``I'd like to talk to Bryce?''  It came out as more of a question than a statement.



``One moment.''



She watched with the phone pressed to one ear as Charlotte recruited some of the older children to prepare dinner.  They started putting things back in cabinets, ordered not by the type of food, but by how long it would last.  One of the children found a cutting board and began to cut lettuce.



``Sierra?''



``Yeah,'' she answered.



``Well?  What do you want?''



``Checking up on you, moron.''



``I'm fine,'' Bryce said.  He managed to sound sullen.



She crossed the room to approach the kitchen counter and mimed proper cutting technique for the ten-year-old that was preparing the lettuce.  It wouldn't do to have the kid lose any fingertips.  Or maybe she was sensitive to the idea while talking to Bryce.



``Is that it?'' Bryce asked.



``I was hoping for more than two words of response.  How's your hand?''



``Hurts.''



``That's going to happen.  You lost all four fingers.''



``No.  It hurts like my fingers are still there and they're being crushed.''



She didn't know what to say to that.  \emph{I'm sorry?  You deserved what you got?}



``Ask Tattletale about it?''



``She's gone.  Has been for more than a day, now.  Jaw said she's not to be disturbed with phone calls or anything like that.''



Skitter had been gone for roughly as long as Tattletale.  According to Charlotte, Skitter had invited a bunch of local villains over and then left shortly after.  They were probably the other eight territory bosses who were working to occupy the city.  That had been over forty-eight hours ago.



``Jaw gave me some painkillers,'' Bryce said.



``What kind?''  Sierra felt a stab of alarm.



It must have been audible, because Bryce replied, ``Relax.  Over the counter stuff.''



``Okay.  What have you been doing?''



``Nothing big.  Keeping track of some members of the Chosen as they move around.  Hookwolf's guys.''



``I know who they are.''



``They've been moving in.  I thought we were going to get in a fight, but Jaw had us all retreat.  I think because I was with them.  It's annoying.''



``It's a \emph{good} thing that you're not being dragged into a firefight.  Especially one with capes.''



``They've been teaching me how to fight with a knife, how to throw one, how to use a gun-''



``I don't want you learning that stuff.''



``I \emph{have to}, in case we get ambushed or something.  And I'm not bad at it.  We could have fought those guys.''



``Did Tattletale tell you that you should fight them?'' she asked, already knowing the answer.



``Like I said, Tattletale isn't around and hasn't been for a while.''



``So the answer is no, she didn't give you the go-ahead.''



``No.''



``That's a good enough reason to back off, then.  I don't know exactly who she is or what she does, but she knows what she's doing.  Trust her in that.''



``Always \emph{awesome} to talk to you, Sierra.  Thanks.  Bye now.''



``Don't hang up on me.  Put me on the phone with Jaw.''



Bryce hung up.



\emph{He's supposed to be getting better, more disciplined.}  Had she made the wrong call?  If Bryce was getting training with guns and knives, and still failing to shape up, this thing with him being recruited by Tattletale could be disastrous in the long run.



She waited a minute, then called the same number.



``Yes?''  Again, Jaw's deep voice.



``He hung up on me.  I wanted to ask you how he was doing.''



``The boy is learning.''



``I'd rather he wasn't learning how to use weapons.  If he's getting in a situation where he needs to fight, you guys aren't keeping your end of the deal.''



``That would be Pritt.  He thinks she's attractive, and listens to her best, so Minor has her accompany him much of the time.  She is a former child soldier, she would have thought self-defense was a good way to regain confidence after the boy lost his fingers.''



She could imagine Jaw saying that with Bryce overhearing, her brother getting simultaneously annoyed and embarrassed.  She liked it.



``Have her cut it out?  I don't want to sound like I'm giving you orders, but I don't want my little brother shooting people.''



``It's fine.  Tattletale told us to do whatever you required as far as the boy is concerned.  I will tell Minor, and he will order the others to keep the boy away from weapons.''



``Thank you.''



``I will also decide on a punishment for the boy for being rude and hanging up on his sister.  I think we would \emph{all} like him to learn some respect for his betters.''



She could imagine him looking at Bryce as he said it.



``Nothing too serious?  As punishment goes?''



``Nothing serious.  It will build character.''



``Thank you.  Any word on what Skitter and Tattletale are doing?''



``No.  All I know is that it will be dangerous, and every squad is on high alert.  We are sleeping in shifts, maintaining combat readiness and doubling patrols.  We were informed three hours ago that the downtown area is off-limits.  I know Lieutenant Fish was deployed there when the order came down, and he has ceased all communications.''



``\emph{All} of downtown?''



``Yes.''



She hung up and headed for the bathroom to tend to the damage her hands had accumulated over the day's work.  Disinfectant, antibiotic ointment, bandages.  Every time she thought she'd found the last small scrape, she found another.



By the time she was done, her hands had as much in the way of bandages as there was exposed skin.  She flexed her fingers to make sure she could still move them, adjusted two bandages, and then returned to the kitchen.



``Progress?''



``Nearly done.  It hasn't cooked very long, and I'm worried it'll just taste like boiled vegetables in water, but you said people were hungry.  How do you want to get the soup out there?''



``There's three spots where people are sleeping tonight.  Let's mobilize the kids and get some food out to everyone.''



``The kids?''



``Everyone needs to contribute.  Maybe if they see seven-year-olds doing their part, the O'Daly clan will get the message.''



``Sierra,'' Charlotte made a pained expression as she spoke, ``They've been through a lot.''



``They're using our sleeping space, they're eating our food supplies.  We can't hold their hands and baby them.  \emph{Everyone's} having a hard time these days.''



``That's cold.''



``Maybe, but I've been working from sunrise to well after dark, here, and they were just sitting around, getting in the way, complaining and crying.''



``Most of their family died just a few days ago.''



Sierra didn't have a response to that.  They were still eating far too much and taking up too much room for people who hadn't lifted a finger to help.  ``Anyways, think I can use the kids?''



``Don't push them.  Some are pretty emotionally sensitive.  But yeah.''



Sierra turned around, ``Hey, munchkins!  Got a job for you.  Help out and we'll give you first dibs on the after-dinner treats!''



Roughly half of the little ones approached her.  Six to ten years old, boys and girls, a variety of ethnicities.



``Who's the oldest?  Raise your hand if you're ten\ldots okay, if you're nine?  Eight?''



She mentally sorted them out, then directed them, ``You, you're in charge of those three.  You're in charge of these two\ldots You're in charge of this pair, okay?''



Older kids looking after little kids.  They sorted into their groups.



``You're carrying soup out to the sleeping areas.  We've got something to carry them in, Charlotte?''



``Yeah.  Just give me a minute.  Don't want them to burn their hands.''



``Everyone carries what they can.  Take the soup out there and then come back here.''



Charlotte put the lids on the first few containers of soup, and the kids scampered off.



Sierra didn't give it a second thought until she heard the shutter sliding open.



``Not the front door!''  Sierra called out, but the kids were already out the front door.  She sighed.



``They're afraid of the storm sewer,'' Charlotte pointed out.



``I know.  It's not that big a deal.  I'm going to go out with the next group, just to keep an eye on the delivery process.''



``Okay.  I'll prep some for you to carry,'' Charlotte said.  ``Find more tupperware or pots I can put this in?''



Sierra nodded and turned to do as she'd been asked, but the kids were already hopping to the task.  She let them go ahead.  It seemed they were glad for something to occupy themselves with.  Maybe they recognized how shitty the overall situation was and they wanted to help fix it.



She suspected she'd find the necessary tupperware faster than the four kids combined, but it wasn't a big deal.



``Well, well, well.''



Sierra whirled around before the man was even finished talking.  Not a man, exactly, but boy didn't fit.



It was Jay.  The Japanese-American boy glared at her through his mop of hair.



``Jay.  You weren't invited here.''



``I can see why.  Electricity, running water, food\ldots you've got it made.  Was wondering where you were going, tried following you, but you disappeared.  Thought we'd missed our chance until we saw some ankle-biters running down the street with plastic containers of food.  Seems you're hoarding the good shit.''



``We're not hoarding,'' she spoke.  She had to swallow to clear her throat.  She knew she had to sound confident, ``This is Skitter's place.''



``Skitter's, sure.  If she's still alive.  But not your space.  Don't see why you can have this stuff and we can't.''



``Skitter gave us permission.''



``We supposed to believe?'' Sugita asked, his voice heavily accented.



``Yeah.''



``No,'' Yan spoke.  She reached behind her back and drew a handgun.  ``Don't believe you.''



\emph{There are kids here}, Sierra thought.



``Stupid,'' she spoke without thinking.



Yan pointed the gun at her.  ``What did you say?''



``You \emph{know} Skitter gave us the go-ahead to use her place.''



``That so?  I overheard someone complaining that Skitter left without announcing anything, after the fires,'' Yan said.  Her tone was mocking.



``You assholes.  Least you can do is drop the bullshit and admit you just want to take our stuff.''



``Was thinking about it, sure,'' Jay said, ``Doesn't look like Skitter's coming back.  Two days, situation like this?  But you're dreaming if you think we're going to just walk away with some food.  I think we're going to evict you.''



``Evict us?



``Move out of the way,'' Yan ordered Sierra, twitching the gun to her left.



``Why?'' Sierra asked.



``Because I'll shoot you if you don't,'' Yan said.  ``I can't believe you're not listening.  You're either stubborn or stupid.''



``I'm tired,'' Sierra replied.  ``And what you're doing here isn't exactly brilliant.  Think about it. Where did this food come from?  The equipment?''



``Skitter bought it.''



``From who?  From where?  It's pretty obvious this place was set up \emph{after} Leviathan came, but where'd she get it?  She had it delivered.  And the same people who make deliveries like this to a supervillain are going to be pretty ticked off if they find out someone's messed with one of their customers.''



The argument was feeble, and she knew it.



``If these people exist, they won't show up tonight.  We'll spend the night.  I figure we're overdue for a party.''



``Leaving us to clean up the mess?''



``Sierra,'' Charlotte spoke, her voice quiet, ``Not worth it.''



Yan gestured with the gun, and Sierra listened this time, stepping out of the way.



Sugita and Jay headed past the counter and into the kitchen, while Yan stood where she could block the front door.  Sierra could see Charlotte shrinking away.  Like a shark that smelled blood, Sugita turned his attention to her.  He stepped close, invading her personal space.



\emph{Don't show fear}, Sierra prayed.



But Charlotte did.  In an instant, it was as though she was a different person than she'd been five minutes ago.  Weak-kneed, cringing, not even resisting as Sugita grabbed at her wrist.



There was something at play there that Sierra hadn't been told about.  ``Leave her alone!''



``Shut up, bitch,'' Yan stepped closer, waggling the gun, ``You want to get shot?''



``Just let us go.  Do whatever the fuck you want here, it's on your head, but let us go.''



``Don't think so.  I hate arrogant bitches.  Going to spoil my mood if I don't do anything about it.  Your choice.  I can shoot you through your palm, shoot you in a knee, or I can shoot one of the kids.''



Sierra glanced at the kids who had shrunk back against counters, cabinets and the wall.  There were tears tracking through the dirt on their faces, but they were mostly managing to keep quiet.



``Well?'' Yan asked, raising her voice.



Sierra couldn't bring herself to speak.  Being shot in the hand- she might never use it again.  But the knee was supposedly the part of the body that had the hardest time recovering from a major injury.



Yan bent down and grabbed one of the oldest boys by the hair.  Ten years old, blond hair in bad need of a cut and a pugnacious nose.  He squealed and writhed in pain at the grip on his scalp, until he wrenched himself out of Yan's grip, falling flat on his back.



The girl jammed the gun in his mouth before he could recover, and he froze.



``Choose!''



``My hand.''



Yan smirked, taking the gun out of the boy's mouth.  ``Put it flat against the wall.''



Sierra started raising her hand, then stopped.



A figure stood behind Yan.  Her costume was barely recognizable – She wore a short cape of tattered black cloth over her body armor, a skintight black suit beneath that, and there were folds of black cloth draped around her legs like a dress or a robe.  The entire fabric seemed to ripple and move.  It took Sierra a second to realize it was crawling with a carpet of insects.



The disconcerting part was the girl's face, or lack thereof.  Her expression was masked behind a shifting mass of bugs that moved in and out of her hairline.  Sierra couldn't even tell where the bugs ended and the scalp began, as the small black bodies crawled into and onto the black curls.  There was a hint of something like glass where Skitter's eyes were, but the bugs ventured far enough over her eyelids and around the frames that nothing was visible in the way of goggles, glasses or skin.



Skitter hadn't made a sound as she entered.  She hadn't spoken, and her footsteps had been quiet.



Yan pointed the gun at Skitter.  ``You're back, huh?''



The villainess didn't speak.  She pointed to her right instead.



Advancing toward the group was a beetle the size of a small pony.  It didn't use its forelimbs to walk, but held them up so the razor edge was both visible and ready to strike.



``Call it off or I shoot!''



``Shoot and you die,'' Skitter's voice was distorted, not really resembling a sound from human lips.  The beetle seemed to offer a deep buzz to accompany the `oo' sounds.  ``It won't be pretty.  Brown recluse venom makes your muscles necrotize.  That means it decays while you're still alive.  It takes days, but the only real cure is taking a knife to the area around the bite.  That might be okay if you have one bite, carve out a half-pound of flesh, let the wound drain, stitch it up.  But what if you have three or four bites?  Or ten?''



``You're bullshitting me,'' Yan spat the words.



Skitter ignored her.  ``It's excruciatingly painful.  Nothing you experienced during your initiation into the ABB even compares, I can guarantee it.  You're rotting alive, your flesh turning black as it liquefies.  So maybe you shoot me.  Maybe you even kill me, though I doubt it.  Either way, whether I walk away from here alive or not, you get bitten.  They're already on you.  All three of you.''



Yan glanced down at her body.  In that same instant, the beetle took flight.  It crossed the room in the span of a heartbeat and slammed into her.  Its blade-like forelimbs caught around Yan and pulled her to the ground.



Sierra turned her attention to the other two, saw Sugita lunging to one side.  She practically threw herself between him and the countertop where the knife still lay on top of the cutting board.  Jay drew his knife, but dropped it in the same motion.  His other hand clutched his forearm as his eyes went wide.



``That's one bite, Shaggy,'' Skitter said.  ``Giving you two seconds to kick the knife under the stove before I give you another.  One-''



Jay kicked the knife across the kitchen floor.  It slid out of sight.



``And you, I think you were the one with the bad accent?  You can step away from Charlotte now.''



Sugita scowled, but he did as he was asked.  He backed away from Charlotte until he stood beside Jay.  Charlotte let one sob escape before she hurried across the kitchen and moved to stand behind Skitter.



\emph{She's been through something, }Sierra thought.  She knew Charlotte was staying in town only because of her family, that she'd been captured by the Merchants and held for at least a short while\ldots and there was some reason she couldn't explain that to her family and just leave the city.



``I hope the rest of you are okay?''  Skitter asked.



``Where were you?'' Sierra returned the question with one of her own.



``Dealing with the Nine.  They're not a concern anymore, at least for now.''



It was surreal, hearing the girl talk about \emph{dealing} with the Slaughterhouse Nine.  They weren't in the same category as your average villain.  They were like monsters from horror films, the killer who always got up at the end of the film, the monster who never died.



``You mean they won't attack anytime soon, or-''



``They're dealt with.  Burnscar's dead.  Crawler's dead.  Mannequin's probably dead.  Cherish and Shatterbird \emph{wish} they were dead.  Found Siberian's weak point, and it'll be international news soon, if it isn't already.  She, Jack and Bonesaw ran.  Tried to pursue, couldn't track them.  It'll be a while before they bounce back.''



``You took on the Nine and won?''



Skitter ventured toward Yan, then used one foot to hold the girl's arm down against the ground.  The beetle pinned it there, pressing the point of one forelimb into her palm with enough pressure that a bead of blood appeared.  Skitter stepped around the girl so the beetle could do the same.  When Yan clenched her fist, Skitter stepped on her fist, crushing it underfoot.



She took her time responding.  When she did speak, all she said was, ``I didn't say we won.''



She lifted her foot, Yan unclenched it, and the beetle stabbed down with another pointed forelimb to pin it to the ground.



``What are you doing?'' Yan asked, a note of desperation in her voice.



Skitter didn't respond.  ``Sierra?  Charlotte?''



Charlotte didn't venture a reply, but Sierra managed one.  ``Yeah?''



Were it not for the accompanying buzz of the bugs, Sierra suspected she wouldn't have heard Skitter speak.  ``You've been working hard.  Thank you.  I didn't expect to have anything to come back to.''



``It's okay,'' Sierra said.  The words were a bit of a non-sequitur, but Skitter seemed to accept them.



``Thought you would have left,'' Skitter said.



``Anyone that's still in the city probably has some reason they can't go.  But things here aren't good.''



``We can fix that,'' Skitter said.  It sounded more like she was talking to herself than to anyone in the room.  It would have been reassuring if she hadn't been staring down at Yan.



``What are you going to do?'' Yan repeated herself.



``Charlotte, would you take the children into another room?''



Charlotte seemed relieved to have the chance to escape.  Every child that was present flocked to her and she hurried into the bedroom.



Yan raised her voice, ``You left!  You abandoned us!''



\emph{They were as insecure as the rest of us,} Sierra thought.  \emph{Not that it excuses their behavior.}



``Hand or knee?'' Skitter asked.



``Fuck you!''  Yan shouted.



Then she convulsed.  She thrashed, dragging her hands against the pointed forelimbs with such violence that she opened ragged cuts in her palms.  She stopped as quickly as she'd started, her eyes going wide.



She'd been bitten, more than once.



``Shaggy-hair, hand or knee?''



Jay's eyes went wide, but he very calmly stated, ``Hand.''



His eyes went wide as a spider crawled down the length of his arm to the back of his hand.  He jumped like he'd been electrocuted.



``And Mr. Accent.  Hand or knee?''



Sugita glanced around, then lunged for Sierra.  Going for the knife on the counter yet again.  She blocked him for the second time, he tried to shove her aside, and she used the distraction to drive her knee into his stomach.  He grunted and folded over.



``Both, then,'' Skitter said.



Sugita was too busy reeling from the knee to the gut to respond or react.



``Attacking my people?  That was dumb.  Attacking a little kid?  Dumber.  Consider my territory to be a \emph{very} bad place to be from now on.  My bugs can see you, they can hear you, and I'll know if you slow down even a little as you leave, give you a few more bites.''



The beetle climbed off Yan, using its forelimbs to pick up the gun by driving the points through the trigger-guard.  It moved to Skitter's side.



Yan, Sugita and Jay all took that as their leave to climb to their feet and head toward the door.  None of them even looked at Skitter, but they stopped when she pushed the door closed.



``There's no safe haven for you in Brockton Bay.  My allies have control of every district, every territory.  No shelter will host you, and our individual forces will be searching every other place you might want to sleep.  Before you get far enough to find a doctor and get those bites treated, my contacts will have spread the word.  The doctors may have to treat you, but we can have our people sitting in the waiting rooms, or working as assistants to the doctors.  If you show your face, you'll get attacked.  Maybe it'll be a direct attack, maybe it won't.  Trust me when I say you won't be in any shape to defend yourselves.''



``So you're condemning us to die?''  Any bravado Yan might have had before had been excised and replaced by wide-eyed fear.



``No.  Leave the city as fast as you can, and you can get help somewhere else.  I don't really care, so long as you're out of my city.  You'll have some ugly scars if you don't hurry.''



Skitter gestured to the door, and the three were quick to leave.  ``Sierra, the shutter.''



She hurried to obey, stepping into the open doorframe and reaching up to bring it down to the ground.  It latched at the door's base.  She shut the door after it.  ``There're kids still on an errand, I think.''



``I'll let you know when to open the shutter again.''



``Okay.''



Skitter scattered the bugs around her face and ran her gloved fingers through her hair to straighten it.  ``I'm sorry.''



``It's okay,'' Sierra replied, not quite sure what the apology was for.



``Couldn't focus on this place and the Nine at the same time, and I thought this place was a lost cause.''



That stung, but Sierra didn't voice the thought.  ``Might be.  We've got bodies to get rid of-''



``I'll handle that tonight.''



``The Chosen have been moving into the edges of your area, here and elsewhere, according to Tattletale's soldier.''



Skitter let herself drop into a chair.  ``Anything serious?  Ongoing attacks?''



``Just occupying the territory, I think.  Maybe making trouble for minorities nearby, but nothing so serious that I've hard about it.''



``Then I'll deal with them after an afternoon's rest.  Maybe open a discussion before I try anything more serious.''  Skitter's voice buzzed as she spoke.  She pulled off the mask that covered the lower half of her face.



``Your voice.  You're still doing the thing where your bugs talk with you.''



``Sorry,'' Skitter said, the swarm suddenly quiet.  ``I don't even think about it anymore.''



``Your gang's a lot smaller.  A lot of people died.''



Skitter put her elbows on her knees, removed her glasses and buried her face in her hands.



\emph{Crying?}



Sierra hesitated.  What was she supposed to do here?



She ventured forward and reached out to put a hand on the girl's shoulder.  She stopped when she saw the carpet of ants, cockroaches and wasps.



``I'm okay,'' Skitter said, without looking up.  She removed her hands from her face and leaned back.  There was no sign of tears – her eyes were dry.  \emph{Just tired}.  ``Could I bother you to make me a cup of tea?  Milk, drop of honey.''



Sierra nodded, ``I remember.''



Silence reigned as she filled the kettle and set it down on the stove.  \emph{Still have to deliver the soup}.  Sierra tried to surreptitiously examine Skitter.  The girl was removing all of the bugs from the surface of her costume and the gaps in the armor.  The swarm flowed up the stairs as a single mass.



``Those three\ldots are they going to die?''



``No.  The bites weren't from a brown recluse.  They'll hurt, they'll swell, and the three will probably leave the city to find a doctor.  Even if they realize I conned them, I think I scared them enough that they won't be coming back to challenge me.''



``Ah.''



\emph{They say we fear the unknown}, Sierra thought to herself.  \emph{So why does she freak me out more as I get to know her?}



She brought her employer tea in the largest cup she'd been able to find.



``Things are going to get better now?'' she asked.  ``You're not worried about the Chosen?''



``No.  I think their leader is gone, and after facing down the Nine, somehow I'm not worried about dealing with them.''



\emph{Facing down the Nine}.  Sierra shivered a bit.



``No,'' Skitter thought aloud.  ``I think the biggest challenge I face comes from \emph{within} our organization.''



That gave Sierra pause.  Had Skitter intended to include her with that `our', or was it just vaguely phrased?



``An ally?  One of the other people with their own territories?''



``I shouldn't have said that,'' Skitter said.



There was a pause.  Sierra thought of how she would excuse herself, go tend to the soup and check on Charlotte, but Skitter spoke first. ``But no.  Not an ally.  At least half of them might get involved, and that could get pretty ugly, fast, but I'm thinking the biggest issue right now is the man at the top.''





